### 2017-02-01 2016-Weak-FH-Bisim/WeakBisim.tex
Moved Week-fh-bisim to github

% !TEX TS-program = pdflatex

\documentclass{lncs/llncs}

\usepackage[T1]{fontenc}
%\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\geometry{a4paper}                   % ... or a4paper or a5paper or ...
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}

%\usepackage{amsfonts}
%\usepackage{fancyhdr}
%\usepackage{cite}
%\usepackage{ifthen}
%\usepackage{amssymb}
%\usepackage{fancyhdr}
%\usepackage{pifont}
\usepackage{stmaryrd}
\usepackage{mathtools,mathpartir}
\usepackage{proof}
%\usepackage{setspace}
%\usepackage{indentfirst}
\usepackage{amsmath,amssymb,amscd,mathrsfs}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
\usepackage{epsfig,color,subfigure,enumitem}
\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
\newcommand{\NOTE}[1]{\textcolor{blue}{\textbf{[NOTE:#1]}}}
\newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
\newcommand{\LUDO}[1]{\textcolor{green}{#1}}
\newcommand{\coloncolon}{{:\hspace{-.2ex}:}}
\makeatletter
\newcommand{\raisemath}[1]{\mathpalette{\raisem@th{#1}}}
\newcommand{\raisem@th}[3]{\raisebox{#1}{$#2#3$}}
\makeatother

\usepackage{macrospNets}

\def\AlgT{\mathcal{T}}
\def\AlgE{\mathcal{E}}
\def\AlgA{\mathcal{A}}
\def\AlgAS{\mathcal{A}_S}
\def\AlgB{\mathcal{B}}
\def\AlgI{\mathcal{I}}

\newcommand{\Pred}{\symb{Pred}}
\newcommand{\Post}{\symb{Post}}
%\usepackage[math]{cellspace}
%\setlength\cellspacetoplimit{ 37pt}
%\setlength\cellspacebottomlimit{18pt}

\pagestyle{plain}

% addition to the mathpartir package for red dotted rules,
% that we use for open-transitions

\makeatletter
\def \dotover {\textcolor{red}{\leavevmode\cleaders\hb@xt@ .22em{\hss $\cdot$\hss}\hfill\kern\z@}}
\def \reddottedrule #1#2{\hbox {\advance \hsize by -0.5em
%\sbox0{$\genfrac{}{}{0pt}{0}{#1}{#2}$} \phantom{\copy0} %
 {\ooalign{\vphantom{$\genfrac{}{}{0pt}{0}{#1}{#2}$}\cr\dotover\cr$\genfrac{}{}{0pt}{0}{#1}{#2}$\cr}}}}

 \def \dottedrule #1#2 {
  {\sbox0{$\genfrac{}{}{0pt}{0}{#1}{#2}$}%
    \vphantom{\copy0}%
    \ooalign{%
      \hidewidth
      $\vcenter{\moveright\nulldelimiterspace
        \hbox to\wd0{%
         \xleaders\hbox{\kern.5pt\vrule height 0.4pt width 1.5pt\kern.5pt}\hfill
          \kern-1.5pt
        }%
      }$
      \hidewidth\cr
    \box0\cr}}
}

\let \defaultfraction \mpr@@fraction
\makeatother

%\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}[theorem]{Proposition}
%\newtheorem{corollary}[theorem]{Corollary}
%\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{algorithm}[theorem]{Algorithm}
%\newtheorem{remark}[theorem]{Remark}
%\newtheorem{definition}[theorem]{Definition}
%\newtheorem{example}[theorem]{Example}
%\newtheorem{problem}[theorem]{Problem}
%\newtheorem{proof}[theorem]{Proof}

% Macros for the SOS rules and proof trees:
%\newcommand\openrule[2]{\redinfer{#1}{#2}}
\newcommand\openrule[2]{\inferrule*[myfraction=\reddottedrule,center]{#1}{#2}}
%\newcommand\openrule[2]{\inferrule*{#1}{#2}}
%\newcommand\ostate[1]{\triangleleft{\;#1\;}\triangleright}
\newcommand\ostate[1]{\triangleleft{#1}\triangleright}
\newcommand{\sm}[1]{\mbox{\boldmath\small #1}}

\title{More equivalences for Open pNets\thanks{This work was partially 
funded by the Associated Team FM4CPS
  between INRIA and ECNU, Shanghai}}
\author{ Ludovic Henrio\inst{1}  \ \ \  Eric Madelaine\inst{1,2} \ \ \ Min Zhang\inst{3}}
\institute{Univ. of Nice Sophia Antipolis, CNRS, UMR 7271, 06900 Sophia Antipolis, France
	\and INRIA Sophia Antipolis M\'edit\'erann\'ee, BP 93, 06902 Sophia Antipolis, France
\and Shanghai Key Laboratory of Trustworthy Computing, ECNU, China}
\date{}                                           % Activate to display a given date or no date

                          % Activate to display a given date or no date

\begin{document}

\maketitle

%\section{}
%\subsection{}

\begin{abstract}
  Strong bisimulation allows to compare open systems described using the pNets model.
  In practice, as happens in process algebras, it is too strong, and
  we need to define some coarser relations, taking into account
  invisible or internal moves.

  Open pNets have a notion of \emph{synchronised actions}
  generalizing the usual internal actions (e.g. $\tau$ of CCS, or $i$
  in Lotos).

  We use this notion to define an equivalence relation similar to
  the classical \emph{weak bisimulation}, and study its properties...

  refinement preorders ?

  Algorithms ?

  Which significant (small) use-case ?

\end{abstract}

\section{Introduction}

\ERIC{imported from FORTE'16, but many of these works also had weak
  version... we need to have another look}

In the nineties, several 
works extended the basic behavioural models based on labelled
transition systems to address value-passing or parameterised systems, using
various symbolic encodings of the
transitions~\cite{deSimone85,Larsen87,HennessyLin:TCS95,Linconcur96}. 
In \cite{Linconcur96}, H.M. Lin addressed value-passing calculi, for which he
developed a symbolic behavioural semantics, and proved algebraic properties.
Separately J. Rathke~\cite{HennessyRathke:TCS98} defined another
symbolic semantics for 
a parameterised broadcast calculus, together with strong and weak bisimulation
equivalences, and developed a symbolic model-checker based on a tableau
method for these processes. 30 years later, no
practical verification approach and no verification platform are
using this kind of approaches to provide proof methods for
value-passing processes or open process expressions.

\paragraph{Contribution}

\paragraph{Related works}

\paragraph{Structure.}

\section{Parameterised Networks (pNets): definition}
\label{section:pnets}

\ERIC{Keep minimum defs here too be independent from FORTE}

This section introduces pNets and the notations we will use in
this paper. Then it gives the formal definition of pNet structures,
together with an operational semantics for open pNets.

pNets are tree-like structures, where the leaves are either
\emph{parameterised labelled transition systems (pLTSs)}, expressing the
behaviour of basic processes, or \emph{holes}, used as placeholders
for unknown processes, of which we only specify the set of possible
actions, this set is named the \emph{sort}.
Nodes of the tree (pNet nodes) are synchronising artifacts, using a
set of \emph{synchronisation vectors} that express the possible
synchronisation between the parameterised actions of a subset of the
sub-trees.

%\smallskip\noindent
\paragraph*{Notations.}
We extensively use indexed structures
over some countable indexed sets, which are equivalent to mappings over
the countable set. % . The indexes will usually be
% integers, bounded or not. Such an indexed family is
%denoted
%follows:
$a_i^{i\in I}$
%, or equivalently  $(i\mapsto a_i)^{i\in I}$
denotes a family of elements $a_i$ indexed over the
set $I$. % Such a family
% is equivalent to the mapping $(i\mapsto a_i)^{i\in I}$.
% To specify the set over which the structure is indexed,
% indexed structures are always denoted with an exponent of the form $i\in I$
% (arithmetic only appears in the indexes if necessary).
$a_i^{i\in I}$ defines both $I$ the set over which the family is
indexed (called \emph{range}), and $a_i$ the elements of the family.
E.g., $a^{i\in\{3\}}$ is the mapping with a single entry $a$ at index
$3$ ; abbreviated $(3\mapsto a)$ in the following.
When this is not
ambiguous, we shall use notations for sets, and typically write
``indexed set over I'' when formally we should speak of multisets, and
write $x\in a_i^{i\in I}$ to mean $\exists i\in I.\, x=a_i$.  An empty
family is denoted $\emptyset$. We
denote classically $\overline{a}$ a family when the indexing set is
not meaningful.  $\uplus$ is the disjoint union on
indexed sets.

% \TODO{Check whether we really use all these notations}

\paragraph*{Term algebra.}
Our models rely on a notion of parameterised actions, that are
symbolic expressions using data types and variables. As our model aims
at encoding the low-level behaviour of possibly very different
programming languages, we do not want to impose one specific algebra
for denoting actions, nor any specific communication mechanism. So we
leave unspecified the constructors of the algebra that will allow building
expressions and actions. Moreover, we use a generic {\em action interaction}
mechanism, based on (some sort of) unification between two or more action
expressions, to express various kinds of communication or
synchronisation mechanisms.

\def\Talg{\mathcal{T}_{\Sigma,\P}}
Formally, we assume the existence of a term algebra $\Talg$,
where $\Sigma$ is the signature of the data and action constructors,
and $\P$ a set of variables. Within $\Talg$, we distinguish a set of
data expressions $\mathcal{E}_\P$, including a set of boolean
expressions $\mathcal{B}_{\P}$ ($\mathcal{B}_{\P}\subseteq\mathcal{E}_\P$).
On top of $\mathcal{E}_\P$ we build the action algebra
$\mathcal{A}_\P$, with $\mathcal{A}_P\subseteq\mathcal{T}_\P,
\mathcal{E}_P\cap\mathcal{A}_P=\emptyset$;
naturally action terms will use data expressions as subterms.
To be able to reason about the data flow between pLTSs, we
distinguish \emph{input variables} of the form $?x$ within terms; the function
$\vars(t)$ identifies the set of variables in a term
$t\in\AlgT$, and $iv(t)$ returns its input variables.

pNets can encode naturally the notion of input actions in value-passing CCS
\cite{Milner89} or of usual point-to-point message passing calculi, but it also allows
for more general mechanisms, like gate negociation in Lotos, or broadcast
communications. Using our notations, value-passing actions \emph{\`a la} CCS would be
encoded as $a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs (in which $v_i$ are 
action terms containing no input variables). 
%For Lotos-style
%distributed synchronisation, we use synchronisation vectors that encode matching data
%offers on a common gate; or 
We can also use more complex action structure such as Meije-SCCS action
monoids, like in $a.b$, $a^{f(n)}$ (see \cite{deSimone85}). The expressiveness of the synchronisation constructs
will depend on the action algebra.

\subsection{The (open) pNets Core Model}
\label{section:pNets}

A pLTS is a labelled transition system with variables; variables can be
manipulated, defined, or accessed inside states, actions, guards, and
assignments. Without loss of generality and to simplify the formalisation, we suppose 
here that 
variables are local to each 
state: each state has its set of variables disjoint from the others. Transmitting 
variable values from one state to the other can be done by explicit assignment. 
%Similarly, to simplify the management of variables and without loss of expressivity, we 
%suppose that transitions looping to the same state does not do assignments.
Note that we make no assumption on finiteness of the set of states nor
on finite branching of the transition relation.

We first define the set of actions a pLTS can use, let $a$
range over action labels, $\symb{op}$ are operators, and $x_i$ range over
variable names. Action terms are:
\[
\begin{array}[l]{rcl@{\quad}p{5.5cm}}
  \alpha\in\AlgA&::=&a(p_1,\ldots,p_n)&\text{action terms}\\
  p_i&::=& ?x~|~\symb{Expr}&\text{parameters (input variable or expression)}\\
  \symb{Expr}&::=& \symb{Value}~|~x~|~\symb{op}(\symb{Expr}_1,..,\symb{Expr}_n)&\text{Expressions}
\end{array}
\]
The input variables in an action term are those marked with a
$\symb{?}$.
We additionally suppose that each input variable does not
appear somewhere else in the same action term:
$p_i=?x\Rightarrow\forall j\neq i.\, x\notin \vars(p_j)$

\begin{definition}[pLTS]
\label{pLTS}
A pLTS is a tuple
$pLTS\triangleq\mylangle S,s_0, \to\myrangle$ where:
\begin{itemize}
\item[$\bullet$]
$S$ is a set of states.
\item[$\bullet$]
$s_0 \in S$ is the initial state.
%\item[$\bullet$]
 %Variables in
%$\iv(\alpha)$ are assigned by the action, other variables can be assigned
%by the additional assignments.
\item[$\bullet$] $\to \subseteq S \times L \times S$ is the transition relation and 
$L$ is the set of labels of the form
$\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in J}\rangle$,
where $\alpha \in\AlgA$ is a parameterised action, $e_b \in
\AlgB$ is a guard, and the variables $x_j\in P$
are assigned the expressions $e_j\in \AlgE$.
If 
$s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
		J}\rangle} s'\in \to $ then $\iv(\alpha)\!\subseteq\! \vars(s')$, 
		$\vars(\alpha)\backslash \iv(\alpha)\!\subseteq\! \vars(s)$, 
		$\vars(e_b)\!\subseteq\! \vars(s')$, and
		$\forall j\!\in\! J .\,\vars(e_j)\!\subseteq\! \vars(s)\land 
		x_j\!\in\!\vars(s')$. %,  and $s= s'\Rightarrow J=\emptyset$.

\end{itemize}
\end{definition}

Now we define
pNet nodes, as constructors for hierarchical behavioural structures.
A pNet has a set of sub-pNets that can be either pNets or pLTSs, and a
set of Holes, playing the role of process parameters.

A composite pNet consists of a set of sub-pNets exposing
a set of actions, each of them triggering internal actions in each of
the sub-pNets. The synchronisation between global actions and
internal actions is given by  \emph{synchronisation vectors}: a
synchronisation vector synchronises one or several internal actions, and
exposes a single resulting global action.
Actions involved at the pNet level (in the synchronisation vectors) do
not need to distinguish between input and output
variables. Action terms for pNets are defined as follows:
\[\begin{array}[l]{rcl@{\quad}l}
  \alpha\in \AlgAS &::=&a(Expr_1,\ldots,Expr_n)
\end{array}
\]

\begin{definition}[pNets]\label{def-pnets}
A pNet is a hierarchical structure where leaves are pLTSs and holes:\\
$\pNet\triangleq pLTS~|~\mylangle \pNet_i^{i\in I}, S_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle$
where
\begin{itemize}
\item[$\bullet$] $I \in \I$ is the set over which sub-pNets are indexed.
\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets.
%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which sub-pNets are indexed.

\item[$\bullet$] $J\in\I_\P$ is the set over which holes are indexed.
$I$ and $J$ are \emph{disjoint}: $I\cap J=\emptyset$,  $I\cup J\neq\emptyset$
\item[$\bullet$] $S_j \subseteq \AlgAS$ is a set of action terms, denoting the $\Sort$ of
hole $j$.

\item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
  synchronisation vectors ($K\in\I_\P$). $\forall k\!\in\! K,
  \symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k$ where
  $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
  $\forall i\!\in\!
  I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$,  $\forall j\!\in\!
  J_k.\,\alpha_{j}\!\in\!S_j$, and $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
  J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
$\Label(\symb{SV}_k) = \alpha'_k$.

\end{itemize}
\end{definition}

The preceding definition relies on the auxiliary functions below:

\begin{definition}[Sorts, Holes, Leaves of pNets]
  \begin{itemize}
  \item The sort of a pNet is its signature, i.e. the set of actions it can
perform. In the definition of sorts, we do not need to distinguish
input variables (that specify the dataflow within LTSs), so for
computing LTS sorts, we use a substitution operator\footnote{$\subst{y_k\gets x_k}^{k\in K}$ is the parallel substitution 
operation.} to remove the
\emph{input marker} of variables. Formally:
\[
\begin{array}{l}
\Sort(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{x \gets ?x| 
x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
		J}\rangle} s'\in \to \} \\ \Sort(\mylangle
\set{\pNet}, \set{\symb{S}}, \set{\symb{SV}}\myrangle) =\{\alpha'_k |\, \alpha_j^{j\in J_k}\to\alpha'_k\in\set{\symb{SV}}\}
\end{array}
\]

\item
The set of holes of a pNet is defined inductively; the sets of holes
in a pNet node and its subnets are all disjoint:
  \[\begin{array}{l}
\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset \\
\Holes(\mylangle \pNet_i^{i\in I}\!,S_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) =J\cup{\displaystyle \bigcup_{i\in I}\Holes(\pNet_i)}\\
\forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
\forall i_1,i_2\in I.\,i_1\neq i_2\Rightarrow  \Holes(\pNet_{i_1})\cap\Holes(\pNet_{i_2})=\emptyset
\end{array}\]
\item
The set of leaves of a pNet is the set of all pLTSs occurring in the structure, defined inductively as:
\[\begin{array}{l}
\Leaves(\mylangle S,s_0, \to\myrangle) \!=\! \{ \mylangle S,s_0, \to\myrangle \}\\
\Leaves(\mylangle \pNet_i^{i\in I}\!,S_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \bigcup_{i\in I}\Leaves(\pNet_i)}
\end{array}\]
\end{itemize}
\end{definition}

A pNet $Q$ is \emph{closed} if it has no hole: $\Holes(Q)=\emptyset$; else it
is said to be \emph{open}.

\begin{figure}[t]
\begin{minipage}{6.1cm}

  \includegraphics[width=\linewidth]{XFIG/Enable1}
  \\[1.3ex]
 \includegraphics[width=\linewidth]{XFIG/Enable2}
  \caption{Two pNet encodings for  Enable }  \label{schema:enable-pnets}
\end{minipage}
  \hspace{2mm}
\begin{minipage}{6cm}
  \includegraphics[width=\linewidth]{XFIG/P-QR}
  \caption{Composed pNet for ``P>>(Q>>R)''}  \label{schema:enable-composed}
\end{minipage}

\end{figure}

\section{Operational Semantics for Open pNets}
\label{section:op-semantics}

The semantics of open pNets will be defined  as an open automaton. An open
automaton is an automaton where each transition composes transitions of several LTSs with
action of some holes, the transition occurs if some predicates hold, and can involve a 
set of state modifications.
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transitions]
	\label{def:OpenTransitions}
	An \emph{open transition} over a set  $(S_i,s_{0 i}, \rightarrow_i)^{i\in
	I}$ of LTSs, a
	set $J$ of holes with sorts $Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is a structure of the form:	
	\begin{mathpar}
	\inferrule*[myfraction=\reddottedrule]
	{\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred, \Post}
	{s \xrightarrow {v}s'}
	\end{mathpar}
	Where $s, s'\in\mathcal{S}$ and for all
        $i\in I$, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the
	LTS $(S_i,s_{0 i}, \rightarrow_i)$, and $\xrightarrow{b_j}_j$
        is a transition of the hole $j$, for any action $b_j$ in the
        sort $Sort_j$. \Pred\ is a predicate
	over the different variables of the
	terms, labels, and states $s_i$, $b_j$, $s$, $v$. \Post\ is a set of equations that 
	hold \emph{after the open transition}, they are represented as a substitution of the 
	form $\{x_k\gets e_k\}^{k\in K}$ 
	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
	variables of the open transition.
\end{definition}

\begin{example}\emph{An open-transition.}
  \label{OT:enable-composed}
  The \texttt{EnableCompL} pNet of Fig. \ref{schema:enable-composed} has 2 controllers and 2 holes. One of its possible open-transition is:

 \smallskip
 $  OT_2  = \openrule{
                       0 \xrightarrow{\delta}_{C_3} 1 ~~
                            0 \xrightarrow{l}_{C_4} 0  ~~                 
                            \xrightarrow{\delta(x4)}_P ~~
                            \xrightarrow{accept(x4)}_Q 
                      }
  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
    {A1_0 \xrightarrow{\underline{\delta(x4)}} A1_1}
  $
\end{example}

\begin{definition}[Open automaton]
	\label{def:open-automaton}
	An \emph{open automaton} is a structure\\ $A =
	<LTS_i^{i\in I},J,\mathcal{S},s_0,\mathcal{T}>$ where:
	\begin{itemize}
		\item[$\bullet$]  $I$ and $J$ are  sets of indices,
		\item[$\bullet$]  $LTS_i^{i\in I}$ is a family of LTSs,
		\item[$\bullet$]   $\mathcal{S}$ is a set of states and $s_0$ an initial state
		among $\mathcal{S}$,
		\item[$\bullet$] $\mathcal{T}$ is a set of open transitions and for each
		$t\in \mathcal{T}$ there exist $I'$, $J'$ with $I'\subseteq I$, $J'
		\subseteq J$, such that $t$ is an open transition over $LTS_i^{i\in I'}$, $J'$,
		and  $\mathcal{S}$.

	\end{itemize}
\end{definition}

%
%Then the semantics of a pNet is characterized by a set of {\em open
%transitions}, where the hypotheses on process parameters are
%replaced by 1) transitions of the pLTSs at the leaves, and 2) formal
%hypotheses on the transitions of the holes. A {\em predicate} is used
%to relate the parameters and names appearing in the actions of the
%leaves and the holes involved in the rules, but also appearing in  the resulting action.

\begin{definition}[States of open pNets]\label{def-states}
  A state of an open pNet is a tuple (not necessarily finite) of the
  states of its leaves (in which we denote tuples
  in structured states as $\triangleleft\ldots\triangleright$ for better readability).

  For any pNet p, let $\overline{Leaves} = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be the set of pLTS at its leaves,
  then $States(p) = \{\triangleleft s_i^{i\in L}
  \triangleright| \forall i\in L. s_i \in S_i\}$.
A pLTS being its own single leave:
  $States(\mylangle S,s_0, \to\myrangle) = \{\triangleleft s \triangleright| s \in S\}$.

The initial state is defined as:
$InitState(p) = \triangleleft {{s_i}_0}^{i\in L}  \triangleright$.
\end{definition}

%% \begin{example} \emph{State of a pNet}
%%   The states of pNet \texttt{EnableCompL} are:
%%   $\triangleleft 00 \triangleright, \triangleleft 10 \triangleright, \triangleleft 11 \triangleright$
%% \end{example}

\paragraph{Predicates:}
Let
$\mylangle\overline{\pNet},\overline{S},\symb{SV}_k^{k\in K} \myrangle$
be a pNet. Consider a synchronisation vector $SV_k$, for $k\in K$. We define a
predicate $\Pred$ relating
the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
\[\Pred(SV_k, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow
\begin{array}{l}
\exists {(a'_i)}^{i\in I},
{(b'_j)}^{j\in J},v'.\, SV_k={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v'
\\~~\land
\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v'
\end{array}\]
In any other case (if the action families do not match or if there is no valuation of
variables such that the above formula can be ensured) the predicate is undefined.

This definition is not constructive but it is easy to build the predicate constructively
by brute-force unification of the sub-pNets
actions with the corresponding vector actions, possibly followed by a simplification
step.

We build the semantics of open pNets as an open automaton where LTSs are the pLTSs at
the leaves of the pNet structure, and the states are given by 
Definition~\ref{def-states}. The open transitions first
 project the global state into states of the leaves, then apply
pLTS transitions on these states, and compose them with the sort of the holes. %The pNet
%structure does not appear in the open-automaton, only the
%set of Holes and the set of Leaves.
The semantics   regularly instantiates \emph{fresh} variables, and uses a
\emph{clone} operator that clones a term replacing each variable with a
fresh one.

\begin{definition}[Operational semantics of open pNets]
	\label{def:operationalSemantics}
	The semantics of a pNet $p$ is an open automaton $A = <Leaves(p),J,\mathcal{S}, s_0,
	\mathcal{T}>$ where:
	\begin{itemize}
		\item $J$ is the indices of the holes: $Holes(p)= H_j^{j\in J}$.
		%  \item $\overline{L}^L = Leaves(p), \overline{H}^J = Holes(p)$
		\item $\overline{\mathcal{S}} = States(p)$ and $s_0 = InitState(p)$
		\item $\mathcal{T}$ is the smallest set of open transitions
		satisfying the rules below:
	\end{itemize}

	%% \TODO{ We should be careful here: after (re) reading "Huimin
	%% 	Lin, 'Symbolic Transition Systems with Assignements', Concur'96" I
	%% 	think handling assignments is not trivial, even for comparisons of pLTSs. }

	The rule for a pLTS $p$  checks that the guard 
	is verified and transforms assignments into post-conditions:

	\begin{description}
		\item[{\bf Tr1:}]
		$\inferrule
		{ s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
					J}\rangle} s'\in \to  }
		{ p = \mylangle  S,s_0, \to \myrangle
			\models
			\inferrule*[myfraction=\reddottedrule]
			{\{s \xrightarrow{\alpha}_p s'\} ,\emptyset ,
			e_b,\left\{x_j\gets e_j\right\}^{j\in J}}
			{\ostate{s} \xrightarrow{\alpha} \ostate{s'}}
		}
		$
	\end{description}
%	Note that this note is greatly simplified by the fact that variables are local to 
%	thread; introducing global state variables or accepting loops to the same 
%	state would 
%	require to reason 
%	on the scope of 
%	each variables, and to introduce additional variables to handle the several occurence 
%	of the same pLTS variable in the predicates. Indeed the constraints on pLTS 
%	transitions 
%	ensure that the same variable never appears both on the left and on the right of the 
%	equations of a predicate.

	The second rule deals with pNet nodes: for each possible
	synchronisation vector applicable to the rule subject, the premisses
	include one {\em open transition} for each sub-pNet involved, one possible
	{\em action} for each Hole involved, and the predicate relating these
	with the resulting action of the vector.
	A key to understand this rule is that the open transitions are
	expressed in terms of the leaves and holes of the pNet structure,
	i.e. a flatten view of the pNet: e.g. $L$ is the index set of the
	Leaves, $L_k$ the index set of the leaves of one subnet, so all $L_k$
	are disjoint subsets of $L$. Thus the states in the open transitions,
	at each level, are tuples including states of all the
	leaves of the pNet, not only those involved in the chosen
	synchronisation vector.

	\begin{description}
		\item[{\bf Tr2:}]
	\end{description}

	\noindent
    $\inferrule
    {k\!\in\! K \\ SV\!\!= \!clone(SV_k) \!=\! \alpha_m^{m \in I_k\uplus J_k} \!\to\! 
    \alpha'_k \\
    	Leaves(p) \!=\! \pLTS_l^{l\in L} \\    	
    	\forall m\in I_k.
    	\pNet_m \models
    	\inferrule*[myfraction=\reddottedrule]
    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \xrightarrow {v_m}
    		\ostate{s_{i}^{\prime\ i \in L_m}}}
    	%\land
    	%Leaves(\pNet_m) = \overline{pLTS}^{L_k})
    	\\
    	I' = \biguplus_{m\in I_k}\!\! I_m'
    	\\ J' = \biguplus_{m\in I_k}\!\! J'_m \uplus J_k 	\\
    	\Pred = \bigwedge_{m\in I_k}\!\! \Pred_m \land
    	\Pred(SV,a_i^{i\in I_k},b_j^{j\in J_k},v)\\
    	\forall j\!\!\in\!\! J_k. {\tt 
    		fresh}(b_j) \\ {\tt fresh}(v) \\ 
    	\forall i\in
    	L\backslash I'.\,s'_i=s_i 
    }
    {p = \mylangle \pNet_i^{i\in I}, S_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\inferrule*[myfraction=\reddottedrule]
    		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I^\prime},
    		\{\xrightarrow{b_j}_j\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_k} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \xrightarrow {v}
    			\ostate{s_i^{\prime i\in L}}}
    	}
    }
    $

	\medskip
%        \TODO{may be explain how $\Pred(SV,a_i^{i\in I_k},b_j^{j\in
%            J_k},v)$ is built ? You mean more than what is written on previous page????}
	%%    \TODO{I have tentatively added the sort constraint on hole actions, that was
	%%not included in the first version... I'm unsure whether this is the best place to
	%%include it, because it may change the decidability conditions on predicates}

\end{definition}
%

\begin{example} \emph{Using the operational rules to compute
    open-transitions}
  In Fig. \ref{usingrules:OT2} we show the deduction tree used to construct and prove the 
  open transition $OT_2$ of \texttt{EnableCompL} (see example page \pageref{OT:enable-composed}).
  The rule uses TR1 for the $\delta$ transition of $C_3$, for the $l$ transition of $C_4$, then combines the result using the $a_4$ vector of the bottom pNet node, and the $\underline{\delta(x)}$ vector of the top node.

\begin{figure}[tb]
\begin{mathpar}
  \small
  \inferrule
    {\inferrule
        {0 \xrightarrow {\delta}_{C_3} 1}
        {C_3
          \models
            \openrule{
              0 \xrightarrow {\delta}_{C_3} 1,\,
              \{\xrightarrow{\delta(x_1)}_P\},\,
              v_1=\delta(x_1)}
                      {\ostate{0}\xrightarrow{v_1}\ostate{1}}
        }\\
%      \sm{fresh}v         \\
      \inferrule%*[right={L_1}]
        {
%          \sm{fresh}{a_Q} \\
          \inferrule
              {0 \xrightarrow{l}_{C_4} 0}
              % {\ostate{0}\xrightarrow{l}\ostate{0}}
              {C_4
                \models
                \openrule{
                      0 \xrightarrow l_{C_4} 0,\,
                      \sm{Pred}_{C_4}}
                      {\ostate{0}\xrightarrow{l}\ostate{0}}
              }
        }
        {
          \textrm{Q>>R}\models
              \openrule
                  { 0 \xrightarrow {l}_{C_4} 0,\,
                    \{\xrightarrow{acc(x_2)}_Q\},\,
                    \ v_2=acc(x_2)
                  }
                  {\ostate{0}\xrightarrow{v_2}\ostate{0}}
        }   
    }
    {
     \textrm{P>>(Q>>R)}
     \models
     \openrule
         { 0 \xrightarrow{\delta}_{C_3} 1, \\ 0 \xrightarrow{l}_{C_4} 0,\\
           \{\xrightarrow{\delta(x)}_P,\,\xrightarrow{acc(x)}_Q\}, \\
            a_3=v_1 \wedge v=a_3 \wedge x_1=x_2
           }
         {\ostate{00} \xrightarrow{v} \ostate{10}}
      }\vspace{-4ex}
\end{mathpar}
  \caption{Proof of transition $OT_2$ (with interaction of processes $P$ and $Q$) for ``P>>(Q>>R)''}
  \label{usingrules:OT2}
\end{figure}

\end{example}

Note that while the scenario above is expressed as a single
instantiation of the possible behaviours, the constructions below are
kept symbolic, and each open-transition deduced expresses a whole family of
behaviours, for any possible values of the variables.

\paragraph{Variable management.}
The variables in each synchronisation vector are considered local:
for a given pNet expression, we must have fresh local variables for
each occurrence of a vector (= each time we instantiate rule
Tr2). Similarly the state variables of each copy of a
given pLTS in the system, must be distinct, and those created for each
application of Tr2 have to be fresh and all distinct. 
This will be implemented within the open-automaton generation algorithm,
e.g. using name generation using a global counter as a suffix.

\subsection{Computing and using open automata}
In this section we present a simple algorithm to construct the open
automaton representing the behaviour of an open pNet, and we prove that
under reasonable conditions this automaton is finite.

\TODO{Eric: refine the algorithm description}

\begin{algorithm}[Behavioural semantics of open pNets: Sketch]
This is a standard residual algorithm over a set of open-automaton
states, but where transitions are open transitions
constructively ``proven'' by deduction trees.

1) Start with a set of unexplored states containing the initial state
of the automaton, and an empty set of explored states.

2) While there are unexplored states:

2a) pick one state from the unexplored set and add it to the explored
set. From this state
build all possible deduction trees by application of the structural
rules Tr1 and Tr2, using all \ERIC{applicable} combinations
of synchronisation vectors.

2b) For each of the obtained deduction trees, extract the resulting
open-transition, with its predicate and \Post\ assignments by exploring the structure of 
the pNet.

2c)
\ERIC{The predicate is submitted to Z3 for checking satisfiability. If it is NOT stisfiable, the resulting OT is discarded. This will minimize the number of
resulting transitions, and potentialy prune the search-space.}

2d)
\ERIC{Optionally, simplify the predicate by eliminating the unnecessary intermediate variables, that were produced as fresh local variables of synchronisation vectors, and fresh result variables of intermediate OTs. In the resulting predicate the only significant variables are :\\
- the input variables of pLTS transitions\\
- the actions of holes\\
- the result action at toplevel.}

For each open-transition,  add the transition in the outgoing transitions of
the current state, and add the
resulting state in the unexplored set if it is not already in the
explored set.

%3) this ends with the "while" from step 2, when we have no more
%unexplored set.
\end{algorithm}

To have some practical interest, it is important to know when this
algorithm terminates. The following theorem shows that an open-pNet
with finite synchronisation sets, finitely many leaves and
holes, and each pLTS at leaves having a finite number of states and
(symbolic) transitions, has a finite automaton:

\begin{theorem}[Finiteness of open-automata.]\\
Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
  J}$, if the sets $L$ and $J$ are finite, if the synchronisation vectors of all pNets 
  included in  $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ 
  are finite, and if
$\forall i \in L.\, finite{(states(pLTS_i))} \text{ and } pLTS_i$
has a finite number of state variables, then Algorithm 1 terminates
and produces an open automaton 
$\mathcal{T}$ with finitely many states and transitions.

% Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in
%     K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
%   J}$,
% build its semantics as in algorithm 1.

% We have:

% $$ finite{(L)} \land finite{(J)} \land \forall i \in L finite{(\{s_i\})}
%   \to finite{(\mathcal{T})}$$
\end{theorem}

\section{Tooling}

\TODO{Eric: high level description of the implementation}

\ERIC{
=> Context VCE, ref to FASE paper\\
=> Current prototype: programatic creation of pNet objects, through the pNet API in VCE. On the middle term, this should be compiled from some language or graphical formalism.\\
=> Open transitions are computed as a direct implementation of the algorithm above. Steps 2a-2b are merged: at each pNet node, after application of rule Tr2, the resulting OT is built from the premisses, without explicitely constructing the deduction tree. \\
=> Variable names are generated for all ``fresh'' and ``clone'' operations, using structured variable names ensuring uniqueness of fresh names, but also reasonable readability of these names for debugging purposes.\\
=> Satisfiability check is done only at toplevel of the deduction tree construction. An alternative would be to submit the satisfiability check to the SMT solver at each level of the tree construction, potentialy reducing the overall number of combinations. But submission to the SMT engine is costly, and more complexity analysis is required before deciding if this would be worthwhile.\\
=> Simplification is not yet implemented. It is not strictly required for the Open Automaton construction, but it will be critical later for predicate comparison in the bisimulation algorithm.}

\TODO{Eric: full result of the tool execution on the running example}

\section{Bisimulation}
\label{section:bisimulation}

	Now we use our symbolic operational semantics to define a notion of
	strong (symbolic) bisimulation. Moreover this equivalence is decidable whenever we 
	have some
	decision procedure on the predicates of the action algebra.

%% , that we prove compatible with the
%% composition of open pNets. \TODO{do we really know this ?}

The equivalence we need is a strong bisimulation between
pNets having exactly the same Holes with the same sorts, but using a
flexible matching 
between open transition, to accommodate comparisons between pNet
expressions with different architectures.
 We name it FH-bisimulation,
 as a short cut for the ``Formal Hypotheses'' manipulated in the
 transitions, but also as a reference to the work of De Simone~\cite{deSimone85},
 that pioneered this idea. Formally:

 \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim}

\noindent
\begin{minipage}{0.69\linewidth} 	Suppose that
   $A_1 = <L_1,J,\mathcal{S}_1, s^1_0,
   \mathcal{T}_1>$ and $A_2 = <L_2,J,\mathcal{S}_2,s^2_0, \mathcal{T}_2>$
   are open automata where the set
   of holes are equal %\LUDO{added:} 
   and of the same sort.  %\LUDO{changed:} 
      Let 
      \ERIC{$\mathcal{R}=\{(s^1,s^2|\Pred_{s^1,s^2})\}$} be a
      relation over the sets 
      $\mathcal{S}_1$ and $\mathcal{S}_2$ 
      constrained by a predicate.  More precisely, for any pair $(s^1,s^2)$, there is a 
      single
      $(s^1,s^2|\Pred_{s^1,s^2})\in\mathcal{R}$  stating that $s^1$ and $s^2$ are related if $\Pred_{s^1,s^2}$\ 
      is 
      true.
\end{minipage}
\hspace{2mm}
\begin{minipage}{0.30\linewidth}
	\includegraphics[width=\linewidth]{XFIG/Bisim}
\end{minipage}
 Then 
   $\mathcal{R}$ is an FH-bisimulation iff for any  states
   $s^1\in\mathcal{S}_1$ and\\ $s^2\in\mathcal{S}_2$, $(s^1,s^2|\Pred)\in\mathcal{R}$, we 
   have
   the following:

 \begin{itemize}
 \item  For any open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \inferrule*[myfraction=\reddottedrule]
         {\{s^1_i\xrightarrow{a_i}_i s^{1'}_i\}^{i\in I_1}, % , s^1_i,s^{1'}_i\in 
         %States(I_1)
           \{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s^1 \xrightarrow {v} s^{1'}}

\end{mathpar}
 there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
 \begin{mathpar}
%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
    \inferrule*[myfraction=\reddottedrule]
         {\{s^{2}_i\xrightarrow{a_{i x}}_i s^{2}_{i x}\}^{i\in I_{2 x}},
           \{\xrightarrow{b_{j x}}_j\}^{j\in J_{2x}}, \Pred_{OT_x},\Post_{OT_x}}
         {s^2 \xrightarrow {v_x} s^{2}_x}
%         \right)
\end{mathpar}
 such that  $\forall x, J_1=J_{2x}, (s^{1'},s^{2}_x|\Pred_{s^{1'},s^{2}_x})\in 
 \mathcal{R}$; 
 and  \\
 $\Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j. b_j=b_{jx}  \Rightarrow \Pred_{OT_x}
     \land v\!=\!v_x \land  
     \Pred_{s^{1'},s^{2}_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
     %     \right)$.

 \item  and symmetrically any open transition from $s^2$ in $\mathcal{T}_2$ can be 
      covered by a set of transitions from $t^1$ in $\mathcal{T}_1$.
 \end{itemize}

 \TODO{Eric: il reste des petits bugs genre $s^{2'}_x$ plutot que
   $s^{2}_x$}

%Where $\symb{Subst}(\Pred,\Post)$ is the parallel substitution of all
%assigned variables.
Two pNets are FH-bisimilar if there exist a relation between their associated 
automata that is an FH-bisimulation and their initial states are equivalent.

 \end{definition}
Classically, $\Pred_{target_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}$
applies in parallel the  
substitutions $\Post_{OT}$ and $\Post_{OT_x}$ (parallelism is crucial
inside each $\Post$ set but $\Post_{OT}$ is independent from
$\Post_{OT_x}$), applying the assignments of the involved rules.

\medskip
\ERIC{If we assume that everything is finite (states and transitions in the
open automata, and the predicates in $\mathcal{R}$, then it is easy to
prove that it is decidable whether a relation is a 
FH-bisimulation provided the logic of the predicates is decidable (see
\cite{Forte2016}). }

\begin{theorem}[Decidability of FH-bisimulation]
Let $A_1$ and $A_2$ be finite open automata
and $\mathcal{R}$ a relation over their states $\mathcal{S}_1$ and
$\mathcal{S}_2$ constrained by a finite set of predicates. Assume that
the predicates inclusion is decidable over  
the action algebra $\mathcal{A}_P$. Then it is decidable whether the relation 
$\mathcal{R}$ is a FH-bisimulation.

\end{theorem}

\section{Composability}

The main interest of our symbolic approach is to define a method to
prove properties directly on open structures, that will be preserved
by any correct instantiation of the holes. In this section we define a
composition operator for open pNets, and we prove that it preserves
FH-bisimulation. More precisely, one can define two preservation
properties, namely 1) when one hole of a pNet is filled by two bisimilar
other (open) pNets; and 2) when the same hole in two bisimilar pNets are
filled by the same pNet, in other words, composing a pNet with two
bisimilar contexts. The general case will be obtained by
transitivity of the bisimulation relation. We concentrate here on the
second property, that is the most interesting.

\begin{theorem}[FH-Bisimulation is an equivalence]\label{thm-equiv} Suppose $\mathcal{R}$ 
is an FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
reflexive, symmetric and transitive.

\end{theorem}

\begin{definition}[pNet composition]
	An open pNet: $\pNet = \mylangle \pNet_i^{i\in I}, S_j^{j\in J}, 
	\overline{\symb{SV}}\myrangle$
 can be (partially) filled by providing  a pNets $\pNet'$ of the
	right sort to fill one of  its holes.	
	Suppose $j_0\in J$:
	%% \[\mylangle \pNet_i^{i\in I},S_j^{j\in J}, \symb{SV}_k^{k\in
	%%   K}\myrangle\left[(\pNet'_i)^{i\in L}\right]= \mylangle \pNet_i^{i\in
	%%   I}\left[(\pNet'_i)^{i\in L}\right]\uplus(\pNet'_i)^{i\in J\cap L},S_j^{j\in 
	%%J\setminus L},
	%% \symb{SV}_k^{k\in K}\myrangle
	%% \]
	\[\pNet\left[\pNet'\right]_{j_0}= \mylangle 
	\pNet_i^{i\in I}\uplus\{j_0\mapsto \pNet'\},S_j^{j\in J\setminus \{j_0\}},
	\overline{\symb{SV}}\myrangle
	\]
\end{definition}

\LUDO{added congruence theorem below}
\begin{theorem}[Congruence]\label{thm-congr-eq}
	Consider an open pNet:
	$\pNet = \mylangle \pNet_i^{i\in I}, S_j^{j\in J}, 
	\overline{\symb{SV}}\myrangle$.
	Let $j_0\in J$ be a hole. Let $Q$ and $Q'$ be two FH-bisimilar pNets such that 
	$\Sort(Q)=\Sort(Q')=S_{j_0}$\footnote{Note that $\Sort(Q)=\Sort(Q')$ is ensured by 
	stronfg bisimilarity.}. Then 
	$\pNet[Q]_{j_0}$ and 
	$\pNet[Q']_{j_0}$ are FH-bisimilar.
\end{theorem}

\begin{theorem}[Context equivalence]\label{thm-ctxt-eq}
	Consider two FH-bisimilar open pNets:
	$\pNet = \mylangle \pNet_i^{i\in I}, S_j^{j\in J}, 
	\overline{\symb{SV}}\myrangle$ and 	$\pNet' = \mylangle {\pNet'}_i^{i\in I}, 
	S_j^{j\in 
	J}, 	\overline{\symb{SV'}}\myrangle$ 
	(recall they must have the same holes to be bisimilar).
	Let $j_0\in J$ be a hole, and $Q$ be a pNet such that $\Sort(Q)=S_{j_0}$. Then $\pNet[Q]_{j_0}$ and 
	$\pNet'[Q]_{j_0}$ are FH-bisimilar.
\end{theorem}

Finally, the previous theorems can be composed to state a general theorem about 
composability and FH-bisimilarity.
\begin{corollary}[Composability]
	Consider two FH-bisimilar pNets with an arbitrary number of holes, when replacing, 
	inside those two original pNets, a subset of the holes by FH-bisimilar pNets, we 
	obtain two FH-bisimilar pNets.
\end{corollary}
%
%In the following we use $\approx$ to denote equality modulo alpha conversion of free 
%variables. In practice, $x\approx y$ can be obtained if: $x=clone(a) \land y=clone(a)$.

\section{Weak bisimulation}

Weak symbolic bisimulation was introduced to relate transition systems
that have indistinguishable behaviour, with respect to some definition
of \emph{invisible actions} that are considered internal to some
subsystem, and consequently cannot be observed, nor used for
synchronisation with their context.
As the notions of invisible action varies in different contexts,
e.g. $tau$ in CCS, and $i$ in Lotos, we will rely here on some set of
\emph{invisible actions} depending on a specific action algebra.

\TODO{we should understand if it make sense to distinguish invisible
  from synchronised actions: in the Forte paper we wrote ``using  as 
\emph{invisible actions} a subset of the
\emph{synchronised actions} defined in Section~\ref{section:pnets}''}.

%% Proving bisimulation properties on our hierarchical broadcast example
%% would take too much space for this paper. Moreover, interesting
%% properties of the HB example would rather be adequate for weak
%% bisimulation, and its large state-space would require some
%% tool-assistance, both for the generation of the open-automata and for
%% their comparison.

Classicaly, we start by defining a derived transition relation based
on sequences of invisible actions:

\begin{definition}[Weak open transitions]
  Let $A = <L,J,\mathcal{S},s_0,\mathcal{T}>$ be an open automaton.
  We define $\mathcal{T^*}$ the \emph{Weak open transition relation}
  with respect to a set of invisible actions $\mathcal{Inv}$ as:

 \begin{mathpar}
 \inferrule*[myfraction=\reddottedrule]
         {\{s_i\xrightarrow{a_i}_i s'_i\}^{i\in I_1}, 
           \{\xrightarrow{b_j}_j\}^{j\in J},\Pred,\Post}
         {s \xRightarrow {v} s'}
         \in \mathcal{T}^*
 \end{mathpar}

 iff there exists a sequence of open transitions
         $OT_x^{x\in X} \subseteq \mathcal{T}$ such that:

 \TODO{Pas si simple !!!}

 \end{definition}

\begin{definition}[Weak FH-bisimulation]\label{def-Weak-bisim}

\noindent
Let $A_1$ and $A_2$ be open automata, and $mathcal{R}$ a relation over
$S_1$ and $S_2$, as in Definition \ref{def-FH-bisim}.

Then 
   $\mathcal{R}$ is an Weak FH-bisimulation iff for any  states
$s^1\in\mathcal{S}_1$ and\\
$s^2\in\mathcal{S}_2$, $(s^1,s^2|\Pred)\in\mathcal{R}$, we 
   have the following:

 \begin{itemize}
 \item  For any open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \inferrule*[myfraction=\reddottedrule]
         {\{s^1_i\xrightarrow{a_i}_i s^{1'}_i\}^{i\in I_1},
           \{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s^1 \xrightarrow {v} s^{1'}}

\end{mathpar}
 there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2^*$:
 \begin{mathpar}
    \inferrule*[myfraction=\reddottedrule]
         {\{s^{2}_i\xrightarrow{a_{i x}}_i s^{2}_{i x}\}^{i\in I_{2 x}},
           \{\xrightarrow{b_{j x}}_j\}^{j\in J_{2x}}, \Pred_{OT_x},\Post_{OT_x}}
         {s^2 \xRightarrow {v_x} s^{2'}_x}
\end{mathpar}
 such that  $\forall x, J_1=J_{2x}, (s^{1'},s^{2'}_x|\Pred_{s^{1'},s^{2'}_x})\in \mathcal{R}$; 
 and  \\
 $\Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
   \left( \forall j. b_j=b_{jx}  \Rightarrow \Pred_{OT_x}
     \land v\!=\!v_x \land  
     \Pred_{s^{1'},s^{2'}_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$

 \item  and symmetrically any open transition from $s^2$ in $\mathcal{T}_2$ can be 
      covered by a set of weak transitions from $t^1$ in $\mathcal{T}_1^*$.
 \end{itemize}

Two pNets are Weak FH-bisimilar if there exist a relation between their associated 
automata that is an Weak FH-bisimulation and their initial sstates are equivalent.

 \end{definition}

\TODO{Here we should include:
  \\  - A definition for Weak FH-Bisimulation
  \\  - A sufficient condition for an open PNet to preserve Weak-FH,
  including: 1) no non-deterministic Tau-choice in the pLTSs, 2) a
  synch vector propagating Tau from a subnet $pNet_i$ mandatory
  everytime $pNet_i$ can do some visible action in the current
  context, 3) if we have a vector <Tau, -, a, - > --> b with ``a'' a visible
  action of some CLOSED subnet, then b=Tau. 
  \\  - the corresponding Congruence theorem
  \\- An example
}

\TODO{Eric: ask Elie, Hubert or others about interesting weak
  equationnal theories for Lotos -- DONE, waiting for answer...}

\TODO{Ludo: ask Simon for weak properties of Bip composition
  ``operators'' -- DONE!}

\section{Conclusion and Discussion}
\label{section:conclusion}

We are currently extending this work,  looking at  both further properties of 
FH-bisimulation, but also
the relations with existing equivalences on closed systems.
We also plan to apply open pNets to the study of complex composition
operators in a symbolic way, for example in the area of parallel
skeletons, or distributed algorithms.
We have started developping some tool support for computing the
symbolic semantics in term of open-automata. The following steps will
be the development of algorithms and tools for checking 
FH-bisimulations, and interfacing with decision engines for
predicates, typically SMT solvers. Those tools will include
an algorithm that partitions the states and generates the right
conditions (automatically or with user input) for checking
whether two open pNets are bisimilar.

Independently, it is clear that most interesting properties of
such complex systems will not be provable by strong bisimulation.
Next steps will include the investigation of weak
versions of the FH-bisimulation, using the notion of
\emph{synchronised actions} mentionned in the paper.
%We are convinced that this work will contribute to the design of tools for
%verifying open distributed systems.

\bibliographystyle{lncs/splncs}

% \bibliography{oasis,biblio}
\bibliography{biblio}

\newpage
\appendix

\section{Proof of associativity of Enable pNet.}
\label{appendix:assoc}

Using the usual encoding of the Lotos Enable operator (see
Fig. \ref{schema:enable-pnets}), we build now open automata for two  
open pNets \texttt{P>>(Q>>R)} and \texttt{(P>>Q)>>R)}, and 
prove their bisimilarity.
\begin{figure}[t]
\centerline{ % \includegraphics[width=0.5\linewidth]{XFIG/Struct-P-QR}
% \includegraphics[width=0.35\linewidth]{XFIG/Struct-PQ-R}}
  \includegraphics[width=0.60\linewidth]{XFIG/P-QR}
  \hspace{5mm}
 \includegraphics[width=0.27\linewidth]{XFIG/PQ-R}}
  \caption{Structure of the pNets for ``P>>(Q>>R) and (P>>Q)>>R''}
  \label{schema:enable-assoc}
\end{figure}

The two open pNets are drawn in Fig. \ref{schema:enable-assoc}. To
alleviate the drawing, we have only 
  given one instance (C2) of the enable controller pLTSs, and one example of
  the set of synchronisation vectors.

  Below we give the two open automata for these pNets. In the
  open-transitions in these 
    automata, the predicates are very simple, and for readability
    we show them directly in the transitions.
    Remark that while the structure of the automaton states is useful
    for their construction, it is not relevant later, so we have
    dropped this structure when drawing the automaton.

\begin{figure}[h]
  \begin{minipage}{2cm}
  \includegraphics[width=\linewidth]{XFIG/PQR-automaton}
  \end{minipage}
  \hspace{10mm}
  \begin{minipage}{7cm}
  \begin{eqnarray*}
    OT_1 & = \openrule{0 \xrightarrow{l}_{C_3} 0
    	\\\xrightarrow{a1}_P\\ a1\neq\delta(x)}
    {\ostate{00} \xrightarrow{a1} \ostate{00}}\\
    OT_2 & = \openrule{
                       0 \xrightarrow{\delta}_{C_3} 1, ~~
                            0 \xrightarrow{l}_{C_4} 0,  ~~                 
                            \{\xrightarrow{\delta(x1)}_P, ~~
                            \xrightarrow{acc(x1)}_Q\}
                      }
                      {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}    \\
    OT_3 & = \openrule{0 \xrightarrow{l}_{C_4} 0,
                        \\1 \xrightarrow{r}_{C_3} 1,\\
                        \xrightarrow{a2}_Q,\\a2\neq\delta(x)
                        }
    {\ostate{10} \xrightarrow{a2} \ostate{10}}\\
    OT_4 & = \openrule{
                       0 \xrightarrow{\delta}_{C_4} 1, \qquad
                       1 \xrightarrow{r}_{C_3} 1, \qquad
                       \{\xrightarrow{\delta(x2)}_Q, \qquad 
                       \xrightarrow{acc(x2)}_R\} 
                       }
                      {\ostate{10} \xrightarrow{\underline{\delta(x2)}} \ostate{11}}    \\
    OT_5 & = \openrule{1 \xrightarrow{r}_{C_3} 1, \\1 \xrightarrow{r}_{C_4} 1, 
    	\\\xrightarrow{a3}_R
    	}
    {\ostate{11} \xrightarrow{a3} \ostate{11}}
    \end{eqnarray*}
  \end{minipage}
  \caption{Open Automaton for the term ``P>>(Q>>R)''}
  \label{schema:enable3bis}
\end{figure}

\begin{figure}[t]
  \begin{minipage}{2cm}
  \includegraphics[width=\linewidth]{XFIG/PQR2-automaton}
  \end{minipage}
  \hspace{10mm}
  \begin{minipage}{7cm}
  \begin{eqnarray*}
    OT'_1 & = \openrule
             {
               0 \xrightarrow{l}_{C_3} 0,~~0 \xrightarrow{l}_{C_4} 0,~~
               \{\xrightarrow{b1}_P\},~~ b1\neq\delta(y)
               }
             {\ostate{00} \xrightarrow{b1} \ostate{00}}\\
    OT'_2 & = \openrule
             {
                       0 \xrightarrow{l}_{C_5} 0, ~~
                       0 \xrightarrow{\delta}_{C_6} 1,  ~~
              \{\xrightarrow{\delta(y1)}_P,~~      \xrightarrow{acc(y1)}_Q\}~~ 
                      }
             {\ostate{00} \xrightarrow{\underline{\delta(y1)}} \ostate{01}}\\
    OT'_3 & = \openrule
             {
               0 \xrightarrow{l}_{C_5} 0,\\0 \xrightarrow{r}_{C_6} 0,
               \\ \{\xrightarrow{b2}_Q\},\\b2\neq\delta(y)
               }
    {\ostate{01} \xrightarrow{b2} \ostate{01}}\\
    OT'_4 & = \openrule
             {
                       0 \xrightarrow{\delta}_{C_5} 1, ~~
                       1 \xrightarrow{r}_{C_6} 1, ~~\{\xrightarrow{\delta(y2)}_Q, ~~
                    \xrightarrow{accept(y2)}_R\} 
                                 }
             {\ostate{01} \xrightarrow{\underline{\delta(y2)}} \ostate{11}}    \\
    OT'_5 & = \openrule
             {1 \xrightarrow{r}_{C_5} 1,\\\{\xrightarrow{b3}_R\}
             	}
             {\ostate{11} \xrightarrow{b3} \ostate{11}}
    \end{eqnarray*}
  \end{minipage}
%  \label{schema:enable5}
\end{figure}

In this example, we have no state variables in the pNets leaves, so we
need no auxiliary predicate in the FH-bisimulation.

Let us build a relation
    $R = \{(A1_0,A2_0), (A1_1,A2_1), (A1_2,A2_2)\}$, and prove that
    $R$ is a strong FH-bisimulation.

    Pick e.g. transition $OT_1$ of automaton $A1$, we have
    $A1_0 \xrightarrow{OT_1}_{A1} A1_0$. The matching transition from
    $A2_0$ is $OT'_1$, with 
    $A2_0 \xrightarrow{OT'_1}_{A2} A2_0$, the set of holes involved in
    both transitions is $\{P\}$, and the resulting state is in the
    bisimulation ($A1_0 ~ A2_0$).
    The proof obligation is:

    $$  a1\neq\delta(x) \implies
         a1=b1 \implies b1\neq\delta(y) \land a1=b1 $$

    The proof obligation for $OT_2$ versus $OT'_2$ is still simpler:

    $$ \delta(x_1)=\delta(y_1) \land acc(x_1)=acc(y_1)
       \implies \underline{\delta(x_1)}=\underline{\delta(y_1)} $$

       the 3 other cases, and the 5 in the other direction, are left
       to the reader. All are simple to prove, so $R$ is a
       FH-bisimulation, and the initial states of the 2 pNets are equivalent.
           \qed

       This proof shows how the flattening induced by the open transitions makes the 
       reasoning on hierarchical structures easy, while keeping a structured view of the 
       compared systems.

       \newpage

       \section{Proofs of basic properties on pNets}
       \subsection{Equivalence relation (Theorem~\ref{thm-equiv})}
        \emph{Suppose $\mathcal{R}$ 
       	is an FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, 
       	$\mathcal{R}$ is 
       	reflexive, symmetric and transitive.
       	}
       \begin{proof}

       It is trivial to check reflexivity and symmetry. Here we focus on the
transitivity. 
To prove transitivity of strong FH-bisimulation on pNets it is sufficient to prove 
transitivity of the strong FH-bisimulation on states. Consider 3 open automata 
$\mathcal{T}_1$, $\mathcal{T}_2$, $\mathcal{T}_3$ and states $s^1$, $s^2$, $s^3$ in those 
automata\footnote{We omit the constraints stating that each $s^i_x$ is in the states of 
$\mathcal{T}_i$ for the sake of readability}.
Suppose we have $\mathcal{R}$ an FH-bisimulation relation between states of 
$\mathcal{T}_1$ and of  $\mathcal{T}_2$; members of $\mathcal{R}$ are of the form 
$(s^1,s^2|\Pred)$.
Suppose we also  have $\mathcal{R}'$ an FH-bisimulation relation between states of 
$\mathcal{T}_2$ and of  $\mathcal{T}_3$; members of $\mathcal{R}2$ are of the form 
$(s^2,s^3|\Pred\,')$.

Let $\mathcal{R}''$ be the relation: 
\[\mathcal{R}'' = \{(s^1,s^3|\Pred\,'')|\,\Pred\,''=\bigvee_{ \begin{array}{l}
(s^1,s^2|\Pred)\in\mathcal{R}\\ (s^2,s^3|\Pred\,')\in\mathcal{R}' 	
\end{array}
}\,\Pred\land\Pred\,'\}\]

The relation is built as follows: for each pair of state $s^1$, $s^3$, for each state 
$s^2$ such that $\mathcal{R}$ relates $s^1$ and $s^2$, and $\mathcal{R}'$ relates $s^2$ 
and $s^3$, we take the conjunction of the two predicates. The predicates for different 
values of $s^2$ are collected by a disjunction.
 we will show
that $\mathcal{R}''$ is an FH-bisimulation. Let
$(s^1,s^2|\Pred)\in\mathcal{R}$,  we have the followings since

\TODO{LUDO: I stopped rewriting here}
For any open transition $OT$ in $\mathcal{T}_1$:

\begin{mathpar}

\inferrule*[myfraction=\reddottedrule]
{\{s^1_i\xrightarrow{a_i}_i s^{1'}_i\}^{i\in I_1}, % , s^1_i,s^{1'}_i\in
	%States(I_1)
	\{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
{s^1 \xrightarrow {v} s^{1'}}

\end{mathpar}

there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:

\begin{mathpar}

%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
\inferrule*[myfraction=\reddottedrule]
{\{s^{2}_i\xrightarrow{a_{i x}}_i s^{2}_{i x}\}^{i\in I_{2 x}},
	\{\xrightarrow{b_{j x}}_j\}^{j\in J_{2x}}, \Pred_{OT_x},\Post_{OT_x}}
{s^2 \xrightarrow {v_x} s^{2}_x}
%         \right)
\end{mathpar}

such that  $\forall x, J_1=J_{2x}, (s^{1'},s^{2}_x|\Pred_{target_x})\in 
\mathcal{R}$;
and  \\

$\Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
\left( \forall j. b_j=b_{jx}  \Rightarrow \Pred_{OT_x}
\land v\!=\!v_x \land
\Pred_{target_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$

for any open transition $OT_x$, since
$(s^2,s^3|\Pred^\prime)\in\mathcal{R}$ there exist open transitions
$OT_{xy}^{x\in X, y\in Y} \subseteq \mathcal{T}_3$:

\begin{mathpar}

%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
\inferrule*[myfraction=\reddottedrule]
{\{s^{3}_i\xrightarrow{a_{i x y}}_i s^{3}_{i xy}\}^{i\in I_{3 xy}},
	\{\xrightarrow{b_{j x y}}_j\}^{j\in J_{3xy}}, \Pred_{OT_{xy}},\Post_{OT_{xy}}}
{s^3 \xrightarrow {v_{xy}} s^{3}_{xy}}
%         \right)

\end{mathpar}
\TODO{LUDO: I have trouble doing computing the next line without intermediates: it is an 
iterative application of many FH bisim definitions with reordering of terms and 
manipulation of quantifiers}
such that  $\forall x, \forall y, J_1=J_{2x}=J_{3xy}, 
(s^{1'},s^{3}_{xy}|\Pred_{target_{xy}})\in \mathcal{R}$; and  \\
$\Pred\,' \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}
\left( \forall j. b_j=b_{jx}=b_{jxy}  \Rightarrow \Pred_{OT_{xy}}
\land v\!=\!v_{xy} \land
\Pred_{target_{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{xy}}}\right)$.

\TODO{the proof is incomplete because it does not deal with predicates and does not 
explicit what is the right $pred''$ $\implies$ TODO}

       \end{proof}

       \bigskip

       The proof of the other theorems rely on two main lemmas,
dealing respectively with the decomposition of a composed behaviour
between the context and the internal pNet, and with their recomposition. 
We start with decomposition: from one open transition of $P[Q]_{j_0}$, we exhibit 
corresponding behaviours of $P$ and $Q$, and determine the relation between their 
predicates:

\begin{lemma}[OT decomposition]\label{lem-decompose} 
	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose:
	\[ P[Q]_{j_0}   % = \mylangle \pNet_i^{i\in I}, S_j^{j\in J}, 
	%\symb{SV}_k^{k\inK}\myrangle
		\models
		{\inferrule*[myfraction=\reddottedrule]
			{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I},
				\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \xrightarrow {v}
				\ostate{s_i^{\prime i\in L}}}
		}
	\]
		with $Q$ ``moving'' (i.e. $J\cap\Holes(Q)\neq\emptyset$ or $I\cap L_Q\neq 
		\emptyset$).
		 Then there exist $v_Q$, $\Pred'$, $\Pred''$, 
		$\Post'$, $\Post''$ s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\inferrule*[myfraction=\reddottedrule]
			{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I\setminus L_Q},
				\{\xrightarrow{b_j}_j\}^{j\in J\setminus \Holes(Q) \cup \{j_0\}}, 
				\Pred',  
				\Post'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \xrightarrow {v}
				\ostate{s_i'^{\, i\in L\setminus L_Q}}}
		}%\]
	\vspace{-2.2ex}\\\text{and~~}
		%\[
		Q\models{\inferrule*[myfraction=\reddottedrule]
			{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I\cap L_Q},
				\{\xrightarrow{b_j}_j\}^{j\in J\cap\Holes(Q)}, \Pred'',  
				\Post''}
			{\ostate{s_i^{i\in L_Q}} \xrightarrow {v_Q}
				\ostate{s_i'^{\, i\in L_Q}}}
		}%\]
		\end{mathpar}
		and  $\Pred\subst{v_Q\leftarrow b_{j_0}} =(\Pred'
		\land \Pred'')$, $\Post=\Post'\uplus 
		\Post''$ where $\Post''$ is the restriction of $\Post$ over variables of 
		$\Leaves(Q)$.
\end{lemma}

   \begin{small}\begin{proof}
       Consider each premise of the open transition (as constructed by rule TR2 in Definition~\ref{def:operationalSemantics}). 
We know each premise is true for $P[Q]_{j_0}$ and try to prove the equivalent premise for 
$P$. 
First, $K$ and the synchronisation vector $SV_k$ are unchanged\footnotemark (however 
$j_0$ passes from 
the set of subnets to the set of holes). Then $SV=clone(\alpha_j^{j\in I_k\uplus\{j_0\}\uplus 
J_k})$. $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$. 
Now focus on OTs of the subnets\footnotemark[\thefootnote]:\\[-2ex]
\[\forall m\in I_k\cup \{j_0\}.
\pNet_m \models
\inferrule*[myfraction=\reddottedrule]
{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m},
	\{\xrightarrow{b_{j}}_j\}^{j\in J_m}, \Pred_m, \Post_m}
{\ostate{s_{i}^{i \in L_m}} \xrightarrow {v_m}
	\ostate{s_{i}^{\prime\ i \in L_m}}}\]
Only elements of $I_k$ are useful to assert the premise for reduction of $P$; the last 
one ensures (note that $Q$ is at place $j_0$, and by definition of the open transition 
for $P[Q]_{j_0}$, $I_{j_0}=I\cap L_Q$, 
$L_{j_0}=L_Q$):\\[-2ex]
	\[Q\models{\inferrule*[myfraction=\reddottedrule]
		{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I\cap L_Q},
			\{\xrightarrow{b_j}_j\}^{j\in J\cap\Holes(Q)}, \Pred_{j_0},  
			\Post''}
		{\ostate{s_i^{i\in L_Q}} \xrightarrow {v_{j_0}}
			\ostate{s_i'^{\, i\in L_Q}}}
	}\]
This already ensures the second part of the conclusion if we 
choose\footnotemark[\thefootnote]  $v_Q=v_{j_0}$ ($\Pred''= \Pred_{j_0}$). Now let $I'= 
\biguplus I'_m=I\setminus L_Q$, $J'=\biguplus J'_m\uplus J_k 
\uplus\{j_0\}=J\setminus\Holes(Q)\uplus \{j_0\}$; the predicate is 
$\Pred'=\bigwedge_{m\in I_k}\Pred_m 
\land \Pred(SV,a_i^{i\in I_k},b_j^{j\in J_k\cup \{j_0\}},v)$
where\footnotemark[\thefootnote] $\Pred(SV,a_i^{i\in I_k},b_j^{j\in 
J_k},v)\Leftrightarrow 
\forall i\in I_k.\, \alpha_i=a_i\land \forall j \in J_k\cup \{j_0\}.\, \alpha_j=b_j \land 
v=\alpha'_k 
$. Modulo renaming of fresh variables, this is identical to the predicate that occurs in 
the source open transition except $\alpha_{j_0}=v_{j_0}$ has been replaced by  
$\alpha_{j_0}=b_{j_0}$.
Thus, $\Pred\subst{v_Q\leftarrow b_{j_0}}=(\Pred' 
\land \Pred'')$. %\TODO{the argument on renaming has mostly been
                 %removed is it still OK? yes.}. 
Finally, Post 
%conditions are easily split\footnote{\TODO{moved. could
%    even remove...?}Note that if the rules are not simplified, no
%  post-condition range over the variables of $P$ and $Q$ at the same
%  time} 
into conditions of the context $P$ and the pNet $Q$ (they are
builts similarly as they only deal with  
leaves): $\Post=\Post'\uplus \Post''$. This concludes the 
proof as we checked all the premises of the open transition for both $P$ and $Q$.\qed
\footnotetext{Cloning and freshness introduce alpha-conversion at many points 
of the proof; we 
	only 
	give major arguments concerning alpha-conversion to make the proof readable; in 
	general, fresh variables appear in each transition inside
        terms $b_j$, $v$, and 
	$\Pred$.}
\end{proof}
   \end{small}

In general, the actions that can be emitted by $Q$ is  a subset of the possible 
actions of the holes, and the predicate involving $v_Q$ and the synchronisation vector is 
 more restrictive than the one involving only the variable $b_{j_0}$. This has no impact 
 on the previous proof and this restriction  results from the composition of predicates.
%\TODO{is this useful? = yes, I think }

Lemma \ref{lem-compose} is combining an open transition of $P$ with
an open transition of $Q$, and building a corresponding transition of
$P[Q]_{j_0}$, assembling their predicates.

\begin{lemma}[Open transition composition]\label{lem-compose} 
	Suppose $j_0\in J$ and:\\[-2ex]
\begin{mathpar}
%\[
P\models{\inferrule*[myfraction=\reddottedrule]
	{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I},
		\{\xrightarrow{b_j}_j\}^{j\in J}, \\\\
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \xrightarrow {v}
		\ostate{s_i'^{\, i\in L}}}
}%\]
\text{~and~}
%\[
Q\models{\inferrule*[myfraction=\reddottedrule]
	{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I_Q},
		\{\xrightarrow{b_j}_j\}^{j\in J_Q},\\\\
		 \Pred',  
		\Post'}
	{\ostate{s_i^{i\in L_Q}} \xrightarrow {v_Q}
		\ostate{s_i'^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Then, we have\\[-2ex]
	\[ P[Q]_{j_0}   % = \mylangle \pNet_i^{i\in I}, S_j^{j\in J}, 
	%\symb{SV}_k^{k\inK}\myrangle
	\models
	{\inferrule*[myfraction=\reddottedrule]
		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I \uplus I_Q},
			\{\xrightarrow{b_j}_j\}^{j\in J\setminus\{j_0\} \uplus J_Q}, 
			\Pred\subst{b_{j_0}\leftarrow v_Q}\land\Pred',  
			\Post\uplus \Post'}
		{\ostate{s_i^{i\in L\uplus L_Q}} \xrightarrow {v}
			\ostate{s_i^{\prime i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}
\begin{small}

\begin{proof}

       Consider each premise of the open transition (constructed by TR2 in 
Definition~\ref{def:operationalSemantics}). 
We know each premise is true for $P$ and try to prove the equivalent premise for 
$P[Q]_{j_0}$ (using the open transition of $Q$). 
$K$ and the synchronisation vector are unchanged ($j_0$ is now in the set of sub-pNets); 
$SV=clone(\alpha_j^{j\in I_k\uplus\{j_0\}\uplus 
	J_k})$. $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$. All subpNets can be 
reduced:\\[-2ex]%\footnote{again we skip arguments related to renaming of fresh 
%variables}:
\[\forall m\in I_k\cup \{j_0\}.
\pNet_m \models
\inferrule*[myfraction=\reddottedrule]
{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I'_m},
	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
{\ostate{s_{i}^{i \in L_k}} \xrightarrow {v_m}
	\ostate{s_{i}^{\prime\ i \in L_k}}}\]
the last sub-pNet is the one filled by $Q$ which offers an open transition by hypothesis.
Let $I'=\biguplus_{m\in I_k} I_m \uplus I_Q = I \uplus I_Q$ and $J'= \biguplus_{m\in I_k} 
J_m \uplus J_Q \uplus J_k = J\setminus\{j_0\}\uplus J_Q$. The predicate for the open 
transition is: $\Pred''=\bigwedge_{m\in I_k}\Pred_m \land \Pred'
\land \Pred(SV,a_i^{i\in I_k}\uplus(j_0\mapsto v_Q),b_j^{j\in J_k},v)$. By definition 
$\Pred(SV,a_i^{i\in I_k}\uplus(j_0\mapsto v_Q),b_j^{j\in J_k},v)\Leftrightarrow
	\forall i\in I_k.\, a_i=\alpha_i\land \forall j \in J_k.\, b_j=\alpha_j \land 
	\alpha'_k=v\land v_Q=\alpha_{j_0}$, finally $\Pred''=\Pred\subst{b_{j_0}\leftarrow 
	v_Q} \land \Pred'$. The post-condition gathers the post-conditions related to all 
	the leaves. Finally, the composed open transition can be
        built. \qed
        \end{proof}
\end{small}

         \newpage
 \section{Proof of Theorem ~\ref{thm-congr-eq}}
 The proof of Theorem~\ref{thm-congr-eq} exhibits classically a bisimulation relation for 
 a 
 composed system.  It considers then an open transition of $P[Q]_{j_0}$ that should be 
 simulated. It then uses  Lemma~\ref{lem-decompose} to decompose the open transition 
 of $P[Q]_{j_0}$ and obtain an open transition of $P$ and $Q$; the FH-bisimulation 
 property can 
 be applied  to $Q$ to obtain an equivalent family of open transitions of $Q'$; this 
 family is 
 then recomposed by Lemma~\ref{lem-compose} to build a set of open transitions of 
 $P[Q']_{j_0}$ 
 that will simulate the original one.

 Let $\Leaves(Q)=p_l^{l\in L}$, $\Leaves(Q')={p'}_l^{l\in L'}$, 
 $\Leaves(P)=p_l^{l\in L_P}$.
 Consider $Q$ FH-bisimilar to $Q'$. It means that there is a relation 
 $\mathcal{R}$ that is an FH-bisimulation between the open automata of the two pNets. 
 We will consider the relation $\mathcal{R}'=\{(s_1,s_2|\Pred)|s_1=s'_1\uplus s \land 
 s_2=s'_2\uplus s \land s\in \mathcal{S}_P \land (s_1',s_2'|\Pred)\in\mathcal{R}\}$ 
 where $\mathcal{S}_S$ is the set of states of the open automaton of $P$.	We will prove 
 that $\mathcal{R}'$ is an open FH-bisimulation. Consider a pair of FH-bisimilar 
 states: $(\ostate{s_{1 i}^{i \in L_P\uplus L}},\ostate{{s}_{2 i}^{i \in L'}\uplus 
 	{s}_{1 i}^{i \in L_P}}|\Pred)\in\mathcal{R}'$. %Those are states of the open 
 %	automata of 
 %	the pNets $P[Q]_{j_0}$ and $P'[Q]_{j_0}$. 
 Consider an 
 open transition $OT$ of $P[Q]_{j_0}$. %We need to find a family ${OT}_x^{x\in X}$ of 
 %	open transitions of $P'[Q]_{j_0}$ that satisfy the conditions of
 %	Definition~\ref{def-FH-bisim}. $OT$ is of the form 
 \\[-2ex]     
 \[P[Q]_{j_0}\models\inferrule*[myfraction=\reddottedrule]
 {\{s_i\xrightarrow{a_i}_i s'_i\}^{i\in I}, % , s^1_i,s^{1'}_i\in 
 	%States(I_1)
 	\{\xrightarrow{b_j}_j\}^{j\in J},\Pred_{OT},\Post_{OT}}
 { \ostate{s_{1 i}^{i \in L_P\uplus L}}\xrightarrow {v} \ostate{{s'}_{1 i}^{i \in 
 			L_P\uplus 
 			L}}}\]
 Let $J'=J\setminus \Holes(Q) \cup \{j_0\}$.	 By 
 Lemma~\ref{lem-decompose} we have :\\[-2ex]
 	\begin{mathpar}
 P\models{\inferrule*[myfraction=\reddottedrule]
 	{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I\setminus L},
 		\{\xrightarrow{b_j}_j\}^{j\in J'}, 
 		\Pred\,',  
 		\Post'}
 	{\ostate{s_{1 i}^{i\in L_P}} \xrightarrow {v}
 		\ostate{s_{1 i}'^{\, i\in L_P}}}
 }\\
 Q\models{\inferrule*[myfraction=\reddottedrule]
 	{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I\cap L},
 		\{\xrightarrow{b_j}_j\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
 		\Post''}
 	{\ostate{s_{1 i}^{i\in L}} \xrightarrow {v_Q}
 		\ostate{s_{1 i}'^{\, i\in L}}}
 }\end{mathpar}
 and  $\Pred_{OT}\subst{v_Q\leftarrow b_{j_0}} =({\Pred\,}'
 \land {\Pred\,}'')$, $\Post_{OT}=\Post'\uplus 
 \Post''$ ($\Post''$ is the restriction of $\Post$ over variables of 
 $\Leaves(Q)$). As $Q$ is FH-bisimilar to $Q'$ and $(\ostate{s_{1 i}^{i \in 
 		L}},\ostate{{s}_{2 i}^{i \in L'}}|\Pred)\in\mathcal{R}$ there is a family 
 $OT'_x$ 
 of 	open transitions of the automaton of $Q'$ such that\\[-2ex] 
 \begin{mathpar}
 Q'\models\inferrule*[myfraction=\reddottedrule]
 {\{s_{2 i}\xrightarrow{a_{i x}}_i s_{2 i x}\}^{i\in I_{x}},
 	\{\xrightarrow{b_{j x}}_j\}^{j\in J\cap\Holes(Q)}, 
 	\Pred_{OT_x},\Post_{OT_x}}
 {\ostate{s_{2 i}^{i\in L'}} \xrightarrow {v_x} \ostate{s_{2 i x}^{i\in L'}}}
 \end{mathpar}
 and  $\forall x, (\ostate{s_{1 i}^{i\in L}},\ostate{s_{2 i x}^{i\in 
 		L'}}|\Pred_{tgt_x})\in 
 \mathcal{R}$; 
 and  \\
 $\Pred \land \Pred\,''
 \Rightarrow \bigvee_{x\in X}
 \left( \forall j\in J\cap \Holes(Q). b_j=b_{jx}  \Rightarrow 
 \Pred_{OT_x}
 \land v_Q\!=\!v_x \land  
 \Pred_{tgt_x}\subst{\Post''}\subst{\Post_{OT_x}}\right)$

 We can now apply Lemma~\ref{lem-compose} on each of the $OT'_x$ together with 
 the transition of $P$ and obtain a new family $OT_x$ of open transitions (where for 
 $i\in L_P$, $s_{2 i}=s_{1 i}$ and $s_{2 i x}=s'_{1 i}$, and for $j\in Holes(P)$, 
 $b_{j x}=b_j$):\\[-2ex]
 \[ P[Q']_{j_0}  
 \models
 {\inferrule*[myfraction=\reddottedrule]
 	{\{s_{2 i}\xrightarrow{a_{i x}}_i {s}_{2 i x}\}^{i\in I_x \uplus 
 			(I\cap L_P)},
 		\{\xrightarrow{b_{j x}}_j\}^{j\in J}, \\
 		\Pred\,'\subst{b_{j_0 x}\leftarrow v_x}\land\Pred_{OT_x},  
 		\Post'\uplus \Post_{OT_x} }
 	{\ostate{s_{2 i }^{i\in L'\uplus L_Q}} \xrightarrow {v_x}
 		\ostate{{s}_{2 i x}^{i\in L'\uplus L_Q}}}
 }
 \]

 Observe that we used the fact that $J=(J\setminus\Holes(Q)\cup 
 \{j_0\})\setminus\{j_0\}\cup 
 (J\cap\Holes(Q))$. Now we have to verify the conditions for the 
 FH-bisimulation between $OT$ and $OT_x$.
 $\forall x, (\ostate{{s'}_{1 i}^{i\in L_P\uplus L}},\ostate{s_{2 i 
 		x}^{i\in L_P\uplus L'}}|\Pred_{tgt_x})\in 
 \mathcal{R}'$ (by definition of
 $\mathcal{R}'$) and in four steps we get:

 \noindent                        
 \begin{small} $\Pred \land \Pred_{OT} \implies
 	\Pred\land(\Pred\,'\land \Pred\,'')\subst{b_{j_0}\leftarrow v_Q}\\ % reversed 
 	%substitution 
 	\implies 
 	(\Pred\land\Pred\,'')\land \Pred\,'\subst{b_{j_0}\leftarrow v_Q}\\ % $b_{j_0}$ only 
 	%appears 
 	%in $\Pred\,'$
 	\implies  \hspace{-2ex}
 	{\displaystyle\bigvee_{x\in X}
 	\left( \forall j\in J\cap \Holes(Q). b_j=b_{jx}  \Rightarrow 
 	\Pred_{OT_x}
 	\land v_Q\!=\!v_x \land  
 	\Pred_{tgt_x}\subst{\Post''}\subst{\Post_{OT_x}}\right)
 }
 \\~\qquad\qquad	\land \Pred\,'\subst{b_{j_0}\leftarrow v_Q} \\
 	\implies
 	 \hspace{-2ex}
 	{\displaystyle\bigvee_{x\in X}
 		\left( \forall j\in J\cap \Holes(Q). b_j=b_{jx}  \Rightarrow 
 		\Pred\,'\subst{b_{j_0}\leftarrow v_x}\land \Pred_{OT_x}
 		\land v_Q\!=\!v_x \land  
 		\Pred_{tgt_x}\subst{\Post''}\subst{\Post_{OT_x}}\right)
 	}
 	$\end{small}

 %\TODO{There was a confusion between the $\Rightarrow$ between the
 %  steps, and the $\implies$ inside the formulas...}

 Explanations: first, we reversed the substitution; then we
 restricted the 
 substitution as $b_{j_0}$ only appears in $\Pred\,'$; then we
 applied the property of FH-bisimulation for $P$ and rearranged the
 terms using the fact that $v_Q=v_x$. The obtained formula reaches the goal except for 
 two points:\\[-4.3ex] 
 \begin{itemize}
 	\item We need $\forall j\!\in\! J$ instead of $\forall j\!\in\! J\cap\Holes(Q)$  but  
 	adding prerequisite on more variables 
 	does not 
 	change the validity of the formula (those variables are not used).
 	\item Concerning the last term, we need 
 	$\Pred_{tgt_x}\subst{\Post_{OT}}\subst{\Post'\uplus \Post_{OT_x}}$ 
 	, i.e.:
 	$\Pred_{tgt_x}\subst{\Post'\uplus 
 		\Post''}\subst{\Post'\uplus \Post_{OT_x}}$. We 
 	can conclude by observing that	$\Pred_{tgt_x}$ does not use any variable of $P$ 
 	and thus $\subst{Post'}$ has no effect.
 \end{itemize}	
 This proves the  condition of the FH-simulation, the other direction is 
 similar.\qed

        \newpage
        \section{Proof of Theorem ~\ref{thm-ctxt-eq}}
The proof of Theorem~\ref{thm-ctxt-eq} exhibits  a bisimulation relation for a 
composed system. It then uses  Lemma~\ref{lem-decompose} to decompose the open transition 
of $P[Q]_{j_0}$ and obtain an open transition of $P$ on which the FH-bisimulation 
property can 
be applied  to obtain an equivalent family of open transitions of $P'$; this family is 
then recomposed by Lemma~\ref{lem-compose} to build a set of open transitions of 
$P'[Q]_{j_0}$ 
that will simulate the original one.

        Let $\Leaves(Q)=p_l^{l\in L_Q}$, 
$\Leaves(P)=p_l^{l\in L}$, $\Leaves(P')={p'}_l^{l\in L'}$.
	Consider $P$ FH-bisimilar to $P'$. It means that there is a relation 
	$\mathcal{R}$ that is an FH-bisimulation between the open automata of the two pNets. 
	We will consider the relation $\mathcal{R}'=\{(s_1,s_2|\Pred)|s_1=s'_1\uplus s \land 
	s_2=s'_2\uplus s \land s\in \mathcal{S}_Q \land (s_1',s_2'|\Pred)\in\mathcal{R}\}$ 
	where $\mathcal{S}_Q$ is the set of states of the open automaton of $Q$.	We will prove 
	that $\mathcal{R}'$ is an open FH-bisimulation. Consider a pair of FH-bisimilar 
	states: $(\ostate{s_{1 i}^{i \in L\uplus L_Q}},\ostate{{s}_{2 i}^{i \in L'}\uplus 
	{s}_{1 i}^{i \in L_Q}}|\Pred)\in\mathcal{R}'$. %Those are states of the open 
%	automata of 
%	the pNets $P[Q]_{j_0}$ and $P'[Q]_{j_0}$. 
Consider an 
	open transition $OT$ of $P[Q]_{j_0}$. %We need to find a family ${OT}_x^{x\in X}$ of 
%	open transitions of $P'[Q]_{j_0}$ that satisfy the conditions of
%	Definition~\ref{def-FH-bisim}. $OT$ is of the form 
\\[-2ex]     
	\[P[Q]_{j_0}\models\inferrule*[myfraction=\reddottedrule]
	{\{s_i\xrightarrow{a_i}_i s'_i\}^{i\in I}, % , s^1_i,s^{1'}_i\in 
		%States(I_1)
		\{\xrightarrow{b_j}_j\}^{j\in J},\Pred_{OT},\Post_{OT}}
	{ \ostate{s_{1 i}^{i \in L\uplus L_Q}}\xrightarrow {v} \ostate{{s'}_{1 i}^{i \in 
	L\uplus 
	L_Q}}}\]
Let $J'=J\setminus \Holes(Q) \cup \{j_0\}$.	 By 
	Lemma~\ref{lem-decompose} we have :\\[-2ex]
			\begin{mathpar}
				P\models{\inferrule*[myfraction=\reddottedrule]
				{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I\setminus L_Q},
					\{\xrightarrow{b_j}_j\}^{j\in J'}, 
					\Pred\,',  
					\Post'}
				{\ostate{s_{1 i}^{i\in L}} \xrightarrow {v}
					\ostate{s_{1 i}'^{\, i\in L}}}
			}\\
			Q\models{\inferrule*[myfraction=\reddottedrule]
				{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I\cap L_Q},
					\{\xrightarrow{b_j}_j\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
					\Post''}
				{\ostate{s_{1 i}^{i\in L_Q}} \xrightarrow {v_Q}
					\ostate{s_{1 i}'^{\, i\in L_Q}}}
			}\end{mathpar}
			and  $\Pred_{OT}\subst{v_Q\leftarrow b_{j_0}} =({\Pred\,}'
			\land {\Pred\,}'')$, $\Post_{OT}=\Post'\uplus 
			\Post''$ ($\Post''$ is the restriction of $\Post$ over variables of 
			$\Leaves(Q)$). As $P$ is FH-bisimilar to $P'$ and $(\ostate{s_{1 i}^{i \in 
			L}},\ostate{{s}_{2 i}^{i \in L'}}|\Pred)\in\mathcal{R}$ there is a family 
			$OT'_x$ 
			of 	open transitions of the automaton of $P'$ such that\\[-2ex] 
			\begin{mathpar}
			%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
			P'\models\inferrule*[myfraction=\reddottedrule]
			{\{s_{2 i}\xrightarrow{a_{i x}}_i s_{2 i x}\}^{i\in I_{x}},
				\{\xrightarrow{b_{j x}}_j\}^{j\in J'}, 
				\Pred_{OT_x},\Post_{OT_x}}
			{\ostate{s_{2 i}^{i\in L'}} \xrightarrow {v_x} \ostate{s_{2 i x}^{i\in L'}}}
			%         \right)
			\end{mathpar}
			and  $\forall x, (\ostate{s_{1 i}^{i\in L}},\ostate{s_{2 i x}^{i\in 
			L'}}|\Pred_{tgt_x})\in 
			\mathcal{R}$; 
			and  \\
			$\Pred \land \Pred'
		 \Rightarrow \bigvee_{x\in X}
			\left( \forall j\in J'. b_j=b_{jx}  \Rightarrow 
			\Pred_{OT_x}
			\land v\!=\!v_x \land  
			\Pred_{tgt_x}\subst{\Post'}\subst{\Post_{OT_x}}\right)$
			%     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x}) \right)$.

			We can now apply Lemma~\ref{lem-compose} on each of the $OT'_x$ together with 
			the transition of $Q$ and obtain a new family $OT_x$ of open transitions (where for 
			$i\in L_Q$, $s_{2 i}=s_{1 i}$ and $s_{2 i x}=s'_{1 i}$, and for $j\in Holes(Q)$, 
			$b_{j x}=b_j$):\\[-2ex]
				\[ P'[Q]_{j_0}   % = \mylangle \pNet_i^{i\in I}, S_j^{j\in J}, 
				%\symb{SV}_k^{k\inK}\myrangle
				\models
				{\inferrule*[myfraction=\reddottedrule]
					{\{s_{2 i}\xrightarrow{a_{i x}}_i {s}_{2 i x}\}^{i\in I_x \uplus 
					(I\cap L_Q)},
						\{\xrightarrow{b_{j x}}_j\}^{j\in J}, \\
						\Pred_{OT_x}\subst{b_{j_0 x}\leftarrow v_Q}\land\Pred\,'',  
						\Post_{OT_x}\uplus \Post''}
					{\ostate{s_{2 i }^{i\in L'\uplus L_Q}} \xrightarrow {v_x}
						\ostate{{s}_{2 i x}^{i\in L'\uplus L_Q}}}
				}
				\]
			Observe that $J=(J\setminus\Holes(Q)\cup \{j_0\})\setminus\{j_0\}\cup 
			(J\cap\Holes(Q))$. Now we have to verify the conditions for the 
			FH-bisimulation between $OT$ and $OT_x$.
			 $\forall x, (\ostate{{s'}_{1 i}^{i\in L\uplus L_Q}},\ostate{s_{2 i 
			x}^{i\in L'\uplus L_Q}}|\Pred_{tgt_x})\in 
			\mathcal{R}'$ (by definition of
                        $\mathcal{R}'$) and in four steps we get:

\noindent                        
\begin{small} $\Pred \land \Pred_{OT} \implies
 \Pred\land(\Pred\,'\land \Pred\,'')\subst{b_{j_0}\leftarrow v_Q}\\ % reversed 
 %substitution 
 \implies 
 (\Pred\land\Pred')\subst{b_{j_0}\leftarrow v_Q}\land \Pred\,''\\ % $b_{j_0}$ only 
 %appears 
 %in $\Pred\,'$
 \implies  \hspace{-2ex}
{\displaystyle{\bigvee_{x\in X}\!(\forall j\!\in\! J'. b_j\!=\!b_{jx}  
\Rightarrow \!
\Pred_{OT_x}\subst{b_{j_0}\!\!\leftarrow\!\! v_Q}
\land v\!=\!v_x}} %\\ \hspace*{40mm} %
\land \Pred_{tgt_x}\subst{\Post'}\subst{\Post_{OT_x}}) \land
\Pred''\\ % 
			%FH for P
 \implies  \hspace{-2ex}
 {\displaystyle{\bigvee_{x\in X}\!( \forall j\!\in\! J'. b_j\!=\!b_{jx} \Rightarrow 
\Pred_{OT_x}\subst{b_{j_0}\!\!\leftarrow\!\! v_Q}\!\land\! \Pred\,''%\\ \hspace*{40mm}
\!\land\! v\!=\!v_x \!\land\!  
\Pred_{tgt_x}\subst{\Post'}\subst{\Post_{OT_x}})}} 			
$\end{small}

%\TODO{There was a confusion between the $\Rightarrow$ between the
%  steps, and the $\implies$ inside the formulas...}

Explanations: first, we reversed the substitution; then we
restricted the 
substitution as $b_{j_0}$ only appears in $\Pred\,'$; then we
applied the property of FH-bisimulation for $P$ and rearranged the
terms. The obtained formula reaches the goal except for two points:\\[-4.3ex] 
\begin{itemize}
	\item We need $\forall j\!\in\! J$ instead of $\forall j\!\in\! J'$ with 
	$J'\!=\!J\!\setminus\! \Holes(Q) \cup \{j_0\}$ but the formula under the quantifier 
	does not depend on 
	$b_{j_0}$ now (thanks to 
	the substitution). Concerning $\Holes(Q)$, adding prerequisite on more variables 
	does not 
	change the validity of the formula (those variables are not used).
	\item We need $\Pred_{tgt_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}\uplus \Post''}$ 
	, i.e.:
	$\Pred_{tgt_x}\subst{Post'\uplus Post''}\subst{\Post_{OT_x}\uplus \Post''}$. We 
	can conclude by observing that	$\Pred_{tgt_x}$ does not use any variable of $Q$ 
	and thus $\subst{Post''}$ has no effect.
\end{itemize}	
This proves the  condition of the FH-simulation, the other direction is 
similar.\qed

  \newpage

  \section{Running example: Hierarchical Broadcast}

Hierarchical Broadcast (HB) is a way of implementing broadcasting
algorithms within a large set of processes, with better performances
and scalability. There have been many proposals for hierarchical
broadcast algorithms (cite...), most of them focussing on specific
architectures or features (in particular fault tolerance), and on
performance analysis. Very few have given a formal description of the
algorithm, allowing to reason about their safety properties.
In this paper, we choose HB as a running example because it is a
complex interaction pattern on which the topology and the
parameterised nature plays a crucial role.

We give here the description of one simple HB algorithm, inspired
from\cite{Taguchi03}. For the formal description, we define a
pNet template, that can be used as a building node in a hierarchical
assembly of processes, organised in a tree of sub-groups. Inside each
sub-group, messages are sent using  local broadcast; associated to
each sub-group is a ``gateway'' in charge of the
transmission of messages, up and down, between the subgroups. The
gateways are described as generic pLTSs, playing the role of
``controllers'' in the pNet node.

\begin{figure}[t]
\centerline{  \includegraphics[width=0.9\linewidth]{XFIG/SchemaHB2}}
  \caption{Principle of a Hierarchical Broadcast structure and protocol}
  \label{fig:hb-scenario}
\end{figure}

Figure \ref{fig:hb-scenario} shows an instantiation of a HB
structure, and a possible scenario:
\begin{itemize}
\item
  The HB tree has 3 sub-groups, each with its gateway process, and 6
  processes scattered in the sub-groups.
\item
  The path in green shows the sequence of message exchanges when Process P21 (within
  group G2) sends a message to process P111 (within group G11).
\item
  As the target is not within the local group to which P21 belongs,
  the initial message $m(111)$ is sent up to group 2, and
  arrives in gateway $gw2$.
\item
  Now the destination belongs to a group that is a sibling of G2, so
  it is broadcast to all its siblings (sent as $bm(111)$, and
  received as $m(111)$). It will be simply discarded by
  gateways or processes that are not involved (here P3), while $gw1$
  will recognize as being of interest, and in next step send it down
  to its group.
\item
  Sending down is again a broadcast, to all members of sub-group
  G1. Process P12 will ignore it, while gateway $gw11$ in turn
  will recognize and forward the message.
\item
  Within group G11, process P111 will finally receives message
  $m(111)$, that terminates our scenario.
\end{itemize}

Along this paper, we will use this example to illustrate the use of
pNets as a structured semantic model, with a stress on the fact that
we represent here HB as a program schema, with unspecified process
arguments, using open pNets. We will show how the symbolic operational
semantics of open pNets computes the dynamics of the HB in term of a
symbolic representation that we call open-transitions, and how we can
prove equivalences between open systems.

\begin{example} \emph{First step: define the action algebra, with data domains,
    operators and predicates.}
  For our HB structure, we use send and receive messages encoded
  respectively as $m(arg)$ and $im(?var)$ with
  $arg$ of type \texttt{Address}. HB has a message-based
  structure, and by convention action names for action reception will
  be prefix by the letter "i". We abstract away
  from the payload of the messages, keeping only target addresses in the HB
  tree as an argument to all messages. Addresses are finite sequences
  of natural numbers written \texttt{s.i}
  with \texttt{s} a sequence and i a number. In concrete instantiations, we
  assume numbers are simple digits, and we write the sequences without
  the dot, as in ``121''. Then in the model of the
  gateways, we must be able to decide whether an address is below/above the
  current address, or in some specific relation, using
  predicates:\\
  - \emph{i==j} Syntactic equality between two sequences.\\
  - \emph{is\_ancestor(i,j)}: $i$ is a (strict) prefix of $j$.\\
  - \emph{is\_direct\_relative(i,j)}: $i$ and $j$ have a common prefix $k$, $i=k.i1$, $j=k.j1$, with $i1$ of length 1, but $j1$ can be of length equal or greater than 1 ($j$ is a brother or a nephew in the genealogy).\\
  - \emph{is\_other\_relative(i,j)}: all other cases.\\
  Note that these 4 predicates are exclusive.
\end{example}

\begin{example}  \emph{Second step: define the gateway behaviour as a pLTS.}

\begin{figure}[h]
\centerline{  \includegraphics[width=0.85\linewidth]{ATG/GatewayHB}}
\caption{Behaviour of a Gateway controller %\TODO{ERIC: change the action syntax}
  }
  \label{fig:hb-HBgateway}
\end{figure}
Figure \ref{fig:hb-HBgateway} shows the pLTS representing the generic
gateway controller. From its initial state, it can receive messages
$ium(?tgt)$ from the subgroup below, or $im(?tgt)$
coming either from above or from an horizontal broadcast. The details will
be explained later, together with the model structure and the
protocol.
To simplify the notation in the pLTS drawings, we use the following
conventions: state variables are implicitely subscripted by the
adequate state number (e.g. $ium(?tgt)$ means $ium(?tgt_2)$), and we
have ``global'' variables that are defined in all states (here $gid$
means $gid_0,gid_1,gid_2$).

Note that we use \texttt{if-then-else} or \texttt{case}
constructs in the pLTS labels. These are mere abbreviations, that can
be expanded as a set of transitions carrying simple labels with adequate guards.
\end{example}

\begin{example} \emph{Sorts of pLTSs:}
  The sort of the gateway in Figure \ref{fig:hb-HBgateway} is:\\
  $\large\{ um(tgt_s), im(tgt_s), dm(tgt_s), bm(tgt_s), um(tgt_s),
  ium(tgt_s), DISCARD, \\ERROR(name) \large\}_{s\in\{1,2\}}$
\end{example}

\begin{figure}[t]
  \includegraphics[width=1.0\linewidth]{ATG/Inst5}
  \caption{A Hierarchical Broadcast pNet Structure}\label{fig:hb-pnet-graphical}
 \end{figure}

\begin{example} \emph{pNet structure, and graphical representation}  
Here we show some parts of the pNet tree expressing our HB
structure. Figure \ref{fig:hb-pnet-graphical} shows the full pNet
model in a graphical format, where each box represents a pNet node
(Groot, G1, ..., G11), a pLTS (gw1, ..., gw11), or a process (P3, ...,
P111).
The actions in the sorts of the nodes appear as ports on the boxes,
and the synchronisation vectors as arrows, or multipoint ``webs''
drawn as ellipses. For
example, the webs
%labelled \texttt{tau}
in the Groot box
  correspond to synchronisation vectors expressing a broadcast
  communication from one of the subnets of Groot (gw1, gw2, or P3), to
  the others.

  Formally, the root pNet has a structure $<gw1, gw2, G1, G2, P3>$,
  with G1 and G2 sub-pNets, their associated gateways gw1, gw2
  pLTSs, and P3 a process Hole. We have 4 possible broadcast communications at the
  root, corresponding to as many synchronisation vectors; e.g. if gw2 is the sender:
  $< im(a), bm(a), -, -, im(a)> \to\!\underline{bm(a)}$.

  We define the synchronisation vectors in a parameterised way
  (independently of a specific HB network configuration) for any
  pNet node in a HB structure. Let $\widetilde{i}$ be the position of this pNet in the
  structure.
   We define here 4 of these synchronisation vectors, that we will
   use in the next sections to illustrate the semantic rules.
   %; the full table is listed in Appendix \ref{Appendix:SynchVectors}.
   In the
  vectors below,
  $\widetilde{I_G}=\{gw\widetilde{i}1,..,gw\widetilde{i}p,G\widetilde{i}1,..,G\widetilde{i}p\}$
   and
  $\widetilde{I_P}=\{P\widetilde{i}1,..,P\widetilde{i}p\}$ are the sets
  containing respectively the indexes of sub-nets and holes of the
  pNet node, $\widetilde{I_{G+P}}$ their union.

  \begin{figure}[h!]
  \label{fig:HBvectors}
  \begin{tabular}{|p{1.4cm}|p{11cm}|}
%% \hline\hline
%% \multicolumn{3}{|l|}{Hierarchical broadcasting}\\
  \hline
  \hline
$(UG)_{\widetilde{i}k}$\newline
 $k\leq g$&\raisebox{-2pt}{
 $\begin{array}[t]{@{}c@{}c@{}c@{}c@{}c@{}c@{}c@{}c@{}}
 &gw\widetilde{i}1,..&,gw\widetilde{i}k,&..,gw\widetilde{i}g,G\widetilde{i}1,..&,G\widetilde{i}k,&..,G\widetilde{i}g,P\widetilde{i}1,..,P\widetilde{i}p\\
<\!& -\,-\,-\    &  ,ium(\widetilde{t}),& -\ -\ -\  &,um(\widetilde{t}),&, -\ -\ -\
&\!>\longrightarrow \underline{um_{\widetilde{i}.k}(\widetilde{t})}
% $
%     \symb{sv}_{u(\widetilde{i}k)}\triangleq
%     <ium_{\widetilde{i}.k}(\widetilde{t})\otimes
%     -^{\widetilde{I_P}}\otimes
%     um_{\widetilde{i}.k}(\widetilde{t})\otimes
%  -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
%         k\}}}>\longrightarrow
%     \underline{um(\widetilde{t})}$
\end{array}$}  \raisebox{-19pt}{~}  \\
\hline
     &{\ERIC{Up gateway}: message m is sent
  up from a group to its gateway, received by the ium action. The
  resulting action is visible as the (synchronised) $\underline{um}$ }\\
\hline
 $(UM)_{\widetilde{i}k}$\newline$k\leq g$
 &\raisebox{-2pt}{$\begin{array}[t]{@{}c@{}c@{}c@{}c@{}c@{}c@{}c@{}c@{}}
 &gw\widetilde{i}1,..&,gw\widetilde{i}k,&..,gw\widetilde{i}g,G\widetilde{i}1,..,G\widetilde{i}g,P\widetilde{i}1,..,P\widetilde{i}p\\
 <\!& -\,-\,-\    &  ,um(\widetilde{t}),& -\ -\ -\   -\ -\ -\
 &\!>\longrightarrow \underline{um(\widetilde{t})}
 \end{array}$}\raisebox{-18pt}{~}\\
\hline
$(UM)_{\widetilde{i}k}$\newline$k\leq p$
&\raisebox{-2pt}{$\begin{array}[t]{@{}c@{}c@{}c@{}c@{}c@{}c@{}c@{}c@{}}
&gw\widetilde{i}1,..,gw\widetilde{i}g,G\widetilde{i}1,..,,G\widetilde{i}g,P\widetilde{i}1,..&,P\widetilde{i}k,&..,P\widetilde{i}p\\
<\!& -\ -\ -\      -\ -\ -\ &,um(\widetilde{t}),&   -\, -\, -
&\!>\longrightarrow \underline{um(\widetilde{t})}
\end{array}$}\raisebox{-18pt}{~}
 % &
%$\symb{sv}_{!\widetilde{i}}\triangleq
%    <um_{\widetilde{i}.k}(\widetilde{t})\otimes
%    -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\otimes
%    -^{\widetilde{I_G}}>\longrightarrow
%    um_{\widetilde{i}.k}(\widetilde{t})$
\\
\hline
     &{\ERIC{Up Message}: message m is sent up from a process
  or a gateway to the enclosing (= parent) group}\\
\hline

%% $(BG)_{\widetilde{k}} \ERIC{HB}$ &
$(HB)_{\widetilde{i}k}$ \newline $k \leq g$
&\raisebox{-2pt}{$\begin{array}[t]{@{}c@{}c@{}c@{}c@{}c@{}c@{}c@{}c@{}}
&gw\widetilde{i}1,...&,gw\widetilde{i}k,&..,gw\widetilde{i}g,&G\widetilde{i}1,..,,G\widetilde{i}g&,P\widetilde{i}1,..,
P\widetilde{i}p \\
<\!& im(\widetilde{t}), .., im(\widetilde{t}) &, bm(\widetilde{t}),& im(\widetilde{t}),
..
im(\widetilde{t}),& -\ -\ -\  &,im(\widetilde{t}),..,im(\widetilde{t})
&\!>\longrightarrow \underline{bm(\widetilde{t})}
\end{array}$}\raisebox{-18pt}{~}
     \\
\hline
     &{\ERIC{Horizontal Broadcast}: message m, from a process or a
  gateway, is broadcast to all its siblings (processes and gateways)
  inside its group}\\
\hline\hline\end{tabular}
\caption{Synchronisation vectors modeling the communication through the HB hierarchy}
\end{figure}

\end{example}

  \begin{example}\emph{An open-transition.}\label{example:open-trans}
	After introducing the operational semantics rules, in example
        \ref{example:deduction-trees}, we shall explain how we 
	construct this transition using the rules.
	The transition below corresponds to the application of vector
        UG at position k=2, and gateway gw2 executing transition
        $0 \xrightarrow{ium(?tgt2_2)}_{gw2} 2$, storing some address in
        the state variable $tgt_2$ of gw2..

	\centerline{
		$\openrule
		{0 \xrightarrow{a}_{gw2} 2 \\
			\xrightarrow{b}_{P21}
			\\ \sm{Pred}_{Root} \\ \emptyset}
		{\ostate{000} \xrightarrow{v} \ostate{020}}
		$
	}

	With the predicates

	$\Pred_{Root} = ( a \!=\! ium(?tgt2_2) \land b\!=\!um(t2) \land b\in
	Sort_{P21} \land t2 = tgt2_2
	\land v \!= \! \underline{um(t2)} )  $
	In the broadcast examples, we do not use assignments and will omit the \Post part of 
	the open transition.
\end{example}

\begin{example} \emph{State of a pNet}
The pNet from Fig. \ref{fig:hb-pnet-graphical} has three leaves (gw1,
gw2, gw11). So its states will be tuples of length 3,
e.g. $\triangleleft 102 \triangleright$.
\end{example}

\begin{example} \emph{Using the operational rules to compute
    open-transitions}
  \label{example:deduction-trees}

To build a proof tree, we have to choose one synchronisation vector at
each instantiation of rule Tr2, and one pLTS transition at each
instantiation of rule Tr1. Each stage in the proof tree builds one
open-transition of the corresponding pNet node.  Let us explain in
detail the first two steps of the
scenario from Fig. \ref{fig:hb-scenario}:

\begin{figure}[h]
\centerline{ \includegraphics[width=5cm]{XFIG/HB2} }
\caption{(open) simplified pNet structure of Hierarchical Broadcast example}
\label{fig:flattening}
\end{figure}

\begin{itemize}
\item Process P21 sends a message towards P111, the combination of sync vectors UM\_21/UG\_2 conveys this message to gateway gw2.
\item The target address is a relative of gateway gw2, so it
  broadcasts the message to its siblings using vector HB\_2.
\end{itemize}
\end{example}

%% \TODO{but not for local variables of a given pLTS, that MUST keep their
%%   names through successive use, to keep the dataflow
%%   information. Still, of course, several instantiations of the same
%%   pLTS (like gw1, gw2) have distinct local varaibles.}

\paragraph{Building the first transition:}

We use instantiations of the synch vector UM at position 21 (that is a
hole), and of UG at position 2 (sub-group SG2 in the broadcast hierarchy) gives us :
\medskip

\noindent
UM\_21 : $< um(t1), - > \to\!um(t1)$\\
UG\_2 : $< -, ium(t2), -, -, um(t2) > \longrightarrow \underline{um(t2)}$

\smallskip\noindent
where the first synch vector (for sub-group SG2) has length 2, and the
second one (for the root pNet) has length 5. Using once the rule Tr1,
and twice rule Tr2, we build a proof tree, in which the premisses
define the behaviour of a gateway pLTS (here
$0 \xrightarrow{ium(?tgt2_2)}_{gw2} 2$, in which $tgt2_2$ stands for
the variable $tgt$ of state 2 in gw2), or of a process at a hole
(e.g. $\xrightarrow{b}_{P21}$ for the process at hole 21).
The conclusion is an open-transition of the root pNet, with the
composite state encoding the states of the 3 gateways at the Leaves,
e.g. $\ostate{000}$.

\begin{mathpar}
  \inferrule
      {\inferrule*
        {0 \xrightarrow{ium(?tgt2_2), True, \emptyset}_{gw2} 2}
        {\sm{gw2} \models
             \openrule {0 \xrightarrow{ium(?tgt2_2)}_{gw2} 2}
                       {\ostate{0} \xrightarrow{ium(?tgt2_2)} \ostate{2} }
             }
        \quad
        \inferrule* [right={[UM\_21]}]
           {
             %\sm{fresh}(b_{P21},v_{SG2})
           }
           {\sm{SG2} \models
             \openrule {\xrightarrow{b}_{P21} \quad \sm{Pred}_{UM\_21}}
                       {\ostate{-} \xrightarrow{v_{SG2}} \ostate{-} }
             }
%           \\ {\sm{fresh}(t1,t2,v) }
           \quad
           \sm{Pred}_{UG\_2}
      }
      {p\_Root
     \models
     \openrule
         {0 \xrightarrow{ium(?tgt2_2)}_{gw2} 2 \\
           \xrightarrow{b}_{P21}
          \\ \sm{Pred1}}
         {\ostate{000} \xrightarrow{v} \ostate{020}}
      }      ~~ [UG\_2]
\end{mathpar}
With:

$Pred_{UM\_21} =  [um(t1)=b \land b\in Sort_{P21} \land um(t1)=v_{SG2}]$

%% $Pred_{UG\_2} = [ium(?t2) = um(t2) \land v_{SG2} = um(t2) ]$

%% $Pred_{Root} = [ium(?t2) = ium(t2) \land b=um(t1) \land
%%   b\in Sort_{P21} \land v_{SG2}=um(t1) \land v_{SG2} = um(t2)
%%   \land v = \tau]  $

$Pred_{UG\_2} = [ium(t2) = ium(?tgt2_2) \land um(t2) = v_{SG2} \land
  v = \underline{um(t2)} ]$

$Pred1 = [Pred_{UM\_21} \land Pred_{UG\_2}]  $

That can be simplified (eliminating the vector local variables and the
intermediate resulting actions), as: $Pred1 = [b\in Sort_{P21}
  \land b=um(tgt2_2) \land v=\underline{b} ]  $

%% \TODO{Beware, problem with the ? of ?tgt2: I would prefer having no
%%   binder (? marker) in the open-automaton predicates, but I do not see
%% yet how the dataflow will be represented there. OOOOps no more input
%% var in this transition, t1 is a variable coming from P21.}

\section{Building more transitions of the HB example:}
\label{appendix:HB-tr2}
Here we detail the construction of the second transition of our
scenario:

\begin{mathpar}
     \openrule
         {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad
           2 \xrightarrow{bm(tgt2_2)}_{gw2} 0 \quad
           \xrightarrow{b}_{P3}
           \quad Pred_{Root}}
         {\ostate{020} \xrightarrow{v} \ostate{100}}
\end{mathpar}
with
$Pred_{Root} = [tgt1_1=tgt2_2 \land b=um(tgt2_2) \land
  b\in Sort_{P3} \land v = \underline{bm(tgt2_2)}]  $

After the first move described in example \ref{example:deduction-trees}, the pLTS of $gw2$ is
in state 2, ready to emit. We build one
open-transition for each item in the case statement of its outgoing
transition; the one we are interested here for our scenario is the
case where the target address is below $gw1$, corresponding to the
predicate [$a$=$bm(tgt2_2)$ $\land$ isDirectRelative(2,$tgt2_2$)], and we
construct the proof tree, reduced here to applications of rule
Tr1 for transitions of the pLTSs gw1 and gw2, and a single application of rule
Tr2 for the synch vector HB at index 2:

\medskip\noindent
HB\_2 : $< im(t3), bm(t3), im(t3) -, - > \longrightarrow \underline{bm(t3)}$

This illustrates the flow of data through sequences of symbolic moves
of our example: in the first open-transition, the value (address) sent
by P21 was stored in the state variable $tgt2_2$. In the second
transition here, synchronisation within the vector HB\_2 yield the
predicate $tgt1_1=tgt2_2$, and thus transfers the address to the state
variable $tgt1_1$ in gw1.

\begin{mathpar}
  \inferrule
      {\inferrule
        {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1}
        { \sm{gw1} \models
          \openrule
              {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad \sm{True}}
              {\ostate{0} \xrightarrow{im(?tgt1_1)} \ostate{1}}
        }
        \\
       \inferrule
           {2 \xrightarrow{bm(tgt2_2)}_{gw2} 0}
           { \sm{gw2} \models
             \openrule
                 {2 \xrightarrow{bm(tgt2_2)}_{gw2} 0 \quad \sm{Pred}_{gw2}}
                 {\ostate{2} \xrightarrow{bm(tgt2_2)} \ostate{0}}
           }
           \quad Pred_{HB\_2}
      }
           {p\_Root
     \models
     \openrule
         {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad
           2 \xrightarrow{bm(tgt2_2)}_{gw2} 0 \quad
           \xrightarrow{b}_{P3}
           \quad Pred2}
         {\ostate{020} \xrightarrow{v} \ostate{100}}}
      ~~ [HB\_2]
\end{mathpar}

$Pred_{gw2} = [\sm{isDirectRelative}(2,tgt2_2)]$

$Pred_{HB\_2} = [im(tgt1_1) = im(t3) \land bm(tgt2_2) = bm(t3) \land b= im(t3) \land b\in Sort_{P3}  \land v = \underline{bm(t3)}]$

$Pred2 = [Pred_{gw2} \land Pred_{HB\_2} ] $

\medskip
This can be simplified, eliminating the intermediate variable $t3$ of vector
HB\_2, while keeping the state variables of $gw_1$ and $gw_2$, the
intermediate $v$ created by Tr2, and the action variable of hole 
$P3$. This yields finally predicate $Pred2$ :

$Pred2 = [tgt1_1=tgt2_2 \land
  b\in Sort_{P3} \land b=um(tgt2_2) \land v = \underline{bm(tgt2_2)}]
$

\medskip
Alternatively, we could also have elimated variable $v$, and directly
show the resulting action $\underline{bm(t3)}]$ in the open
  transition. This is slightly more compact, and maybe more readable,
  so we shall use this way in the open-automaton below.

\newpage

Below we show the initial transitions of the automaton of our HB
system. The full open-automaton has 17 states, and we have not
computed by hand its full set of transitions. This work would be very
tedious with pen and paper; we are currently developping a software
tool to this end.

\begin{figure}[h]
  \includegraphics[width=0.35\linewidth]{XFIG/HB2}
\end{figure}

In this open-automaton, we have simplified the predicates and
eliminated the local variables, excepted those from the occurences of
the pLTS gw1 and gw2, and from the behaviour of holes.

\begin{figure}[h]
  \includegraphics[width=\linewidth]{XFIG/HB-OpenAut}
\end{figure}
\newpage

\begin{eqnarray*}
OT_1 & = \openrule
         {0 \xrightarrow{ium(?tgt2)}_{gw2} 2 \quad
           \xrightarrow{b1}_{P21}
          \quad P1}
         {\ostate{000} \xrightarrow{um(tgt2_2)} \ostate{020}}\\
 with & P1 = [b1\in Sort_{P21} \land b1=um(tgt2_2) ]
 \\
OT_2 & = \openrule
         {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad
           2 \xrightarrow{bm(tgt2_2)}_{gw2} 0 \quad
           \xrightarrow{b2}_{P3}
           \quad P2}
         {\ostate{020} \xrightarrow{\underline{bm(tgt2_2)}} \ostate{100}}\\
         with & P2 = [tgt1_1=tgt2_2 \land IsDirectRelative(2,tgt2_2)
           \land  b2\in Sort_{P3} \land b2=um(tgt2_2) ]
         \\
OT_3 & = \openrule
         {1 \xrightarrow{dm(tgt1_1)}_{gw1} 0 \quad
           0 \xrightarrow{im(?tgt11_1)}_{gw11} 1 \quad
           \xrightarrow{b3}_{P12}
           \quad P3}
         {\ostate{100} \xrightarrow{\underline{dm(tgt1_1)}} \ostate{001}}\\
         with & P3 = [tgt11_1=tgt1_1 \land IsAncestor(1,tgt1_1)
           \land  b3\in Sort_{P12} \land b3=im(tgt1_1) ]
         \\
OT_4 & = \openrule
         { 1 \xrightarrow{dm(tgt11_1)}_{gw11} 0 \quad
           \xrightarrow{b4}_{P111}
           \quad P4}
         {\ostate{001} \xrightarrow{\underline{dm(tgt11)}} \ostate{000}}\\
 with & P4 = [ b4=im(tgt11_1) \land  b4\in Sort_{P111} \land IsAncestor(11,tgt11_1) ]
         \\
OT_5 & = \openrule
         {1 \xrightarrow{Discard}_{gw1} 0 \quad
           \quad P5}
         {\ostate{100} \xrightarrow{\underline{Discard}} \ostate{000}}\\
 with & P5 = [IsDirectRelative(1,tgt1_1) ]
 \\
OT_6 & = \openrule
         { 2 \xrightarrow{Discard}_{gw2} 0 \quad
           \quad P6}
         {\ostate{020} \xrightarrow{\underline{Discard}} \ostate{000}}\\
 with & P6 = [ IsAncestor(2,tgt2_2) ]
 \\
OT_7 & = \openrule
         {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad
          0 \xrightarrow{im(?tgt2_1)}_{gw2} 1 \quad
          \xrightarrow{b7}_{P3}\quad
           \quad P7}
         {\ostate{000} \xrightarrow{im(?a)} \ostate{110}}\\
 with & P7 = [ tgt1_1 = tgt2_1 = a \land b7\in Sort_{P3} \land b7 = im(?a)  ]
 \\
OT_8 & = \openrule
         {2 \xrightarrow{Discard}_{gw2} 0 \quad
           \quad P8}
         {\ostate{110} \xrightarrow{Discard} \ostate{100}}\\
 with & P8 = [ IsDirectRelative(2,tgt2_1) ]
\end{eqnarray*}

\end{document}

\section{Discussion on substitution, matching, unification}

\TODO{I think appendices B and C must be removed from the submission
  (;-). Do we need anything else as an appendix ? Maybe some of the
  details on Hierarchical Braodcast, when we will deal with the space limit...}

\TODO{this is far from being final... What should we leave here
  ? a generic definition of what must be part of the Action Algebra
  definition, substitution, protected variables; and
  move to other sections the application and examples of these.
In fact we currently do not use any notion of substitution, nor
protect variables. Only these predicates, built as sets of equations,
with a lot of fresh variables...}

\ERIC{[this text in blue is NOT supposed to stay here as such. Just
    guidelines towards identifying what we need to set up]
  To define the operational semantics of pNets, we need only two core
operations on action expressions: specialisation and unification.
\begin{itemize}
\item when composing pNets, substituting a pNet for a hole, each action in
the subnet sort has to match one action of the hole sort, but may be
more specific (substitution).
\item when building a proof tree from a synch vector, we collect a
  number of substitutions from the involved processes, and we have to
  match them with the action expressions in the vector. The result is
  a substitution for the variables of the global action, together with
  a predicate, built from the guards of the controllers and predicates
  of the subnets.
\end{itemize}
In some cases, substitutions are results of full unification between
action expressions, but in other cases it may be disymetric in the
sense that some variables can be substituted, and other not. We can
formalise this in term of ``protected variables'' in the unification,
opposed to ``input variables'' that can be arbitrarily substituted (=
can accept any value, like in classical value-passing algebra communication).}

\section{Future papers...}

I removed from here all appendices that were not directly related to this paper.
They will be providing subjects for future research (internships ?) and future papers, including:

\begin{itemize}
  \item Is open (strong) bisim compatible with pNet composition operator (as defined in PdP paper) ?
  \item Is Open-bisimulation compatible with closed bisimulation ?
    \item Effective algorithm for 1) checking strong bisimulation (given a state partition) 2) computing the coarsest partition (if it exists).
\item Model-checking Open-Automata:
This may come to be simpler to define and implement than FH-bisimulation.
\item FH-Refinement (and maybe even weak bisimulation if we do not find the time and/or space to have it here)
\item Fulll use-case on Hierarchical Broadcast
\end{itemize}

\section{Full definition of the HB pNet model}
\label{Appendix:SynchVectors}

  The table in Fig. \ref{fig:HBvectors} lists the synchronisation
  vectors used in all 3 algorithms and their variants. The vector
  naming schema is the following: the first letter encodes the direction
  of the message: U(p), D(own), H(orizontal); the second letter its
  type: B(roadcast) G(gateway-group) or M(simple message).

  Additionally, there are 2 special vectors, DIS for (silent) Discard
  events, and ERR for (visible) Error events.

  Among the 6 basic vectors, 3 of them (UG, DG, UM) are shared by all
  algorithms, DB is used by Full and hierarchical braodcast, while the
  last 2, HM and HB are specific to horizontal messages of Unicats and
  hierarchical brodcast respectively.

  \TODO{missing the variants here...}

\begin{figure}[h!]
  \label{fig:HBvectors}
\begin{tabular}{|p{1.6cm}|p{8.8cm}|l|}
%% \hline\hline
%% \multicolumn{3}{|l|}{Hierarchical broadcasting}\\
  \hline
  \hline
\multicolumn{3}{|p{12cm}|}{\ERIC{Need a short explanation about notations here: indices, indexed actions to be instanciated to match the terms in the sorts, ...? }}\\
  \hline
 %% $(UC)_{\widetilde{k}} \ERIC{UG}$ & $
 $(UG)_{\widetilde{k}}$ & $
     \symb{sv}_{u(\widetilde{i}.k)}\triangleq
     <?um_{\widetilde{i}.k}(\widetilde{t})\otimes
     -^{\widetilde{I_P}}\otimes
     !m_{\widetilde{i}.k}(\widetilde{t})\otimes
     -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
         k\}}}>\longrightarrow \tau(
     m_{\widetilde{i}.k}(\widetilde{t}))$ &
     $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}$\\
\hline
     &\multicolumn{2}{|p{10cm}|}{\ERIC{Up gateway}: message m is sent up from a group to its gateway}\\
\hline
%% $(DG)_{\widetilde{k}} \ERIC{DB}$&
$(DB)_{\widetilde{k}}$&
$\symb{sv}_{?\widetilde{i}}\triangleq
     <?m_{\widetilde{i}.k}(\widetilde{t})\otimes
     -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\otimes
     -^{\widetilde{I_G}}>\longrightarrow
     ?dm_{\widetilde{i}}(\widetilde{t})$&$\widetilde{k}=\widetilde{i}.k\in \widetilde{I_{G+P}}$\\
     \hline
     &\multicolumn{2}{|p{10cm}|}{\ERIC{Down Broadcast}: a message m received by a group is
       forwarded (broadcast) to all elements of the group, meaning to
       all processes and gateways inside.}\\
\hline
$(UM)_{\widetilde{k}}$&
$\symb{sv}_{!\widetilde{i}}\triangleq
    <!um_{\widetilde{i}.k}(\widetilde{t})\otimes
    -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\otimes
    -^{\widetilde{I_G}}>\longrightarrow
    !um_{\widetilde{i}.k}(\widetilde{t})$ & $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_{G+P}}$\\
\hline
     &\multicolumn{2}{|p{10cm}|}{\ERIC{Up Message}: message m is sent up from a process
  or a gateway to the enclosing (= parent) group}\\
\hline

%% $(BG)_{\widetilde{k}} \ERIC{HB}$ &
$(HB)_{\widetilde{k}}$ &
$\symb{sv}_{b(\widetilde{i}.k)}\triangleq
    <?m_{\widetilde{i}.j}^{\forall j\in I_K}(\widetilde{t})
    \otimes !bm_{\widetilde{i}.k}(\widetilde{t})
    \otimes -^{\widetilde{I_G}}>\longrightarrow \tau( bm(\widetilde{t}))$ &
    $I_K = \{k/\widetilde{i}.k\in \widetilde{I_{G+P}}\}$, \\ &  &  and
    $\widetilde{k}=\widetilde{i}.k$ \\
\hline
     &\multicolumn{2}{|p{10cm}|}{\ERIC{Horizontal Broadcast}: message m, from a process or a
  gateway, is broadcast to all its siblings (processes and gateways)
  inside its group}\\

\hline
%% $(DC)_{\widetilde{k}} \ERIC{DG}$ &
$(DG)_{\widetilde{k}}$ &
$\symb{sv}_{?\widetilde{i}}\triangleq
     <!dm_{\widetilde{i}.k}(\widetilde{t})\otimes
     -^{\widetilde{I_P}}\otimes
     ?dm_{\widetilde{i}.k}(\widetilde{t})\otimes
     -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}}
     >\longrightarrow
     \tau(m_{\widetilde{i}.k}(\widetilde{t}))$,
%      <?m_{\widetilde{i}.k}^{\forall k\in
%        I_K}(\widetilde{t})\otimes
%      -^{\widetilde{I_P}}\otimes -^{\widetilde{I_G}}>\longrightarrow
     %      ?m_{\widetilde{i}}(\widetilde{t})$
     & $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}$\\

\hline
     &\multicolumn{2}{|p{10cm}|}{\ERIC{Down Gateway}: message $m$ is sent down from a gateway
to the corresponding subgroup; it should then be forwarded inside the
subgroup, e.g. with $(DM)_{\widetilde{k}}$}\\
\hline
%% $(DK)_{\widetilde{k}} \ERIC{DM}$&
$(DM)_{\widetilde{k}}$&
$\symb{sv}_{!\widetilde{i}}\triangleq
    <  ?m_{\widetilde{i}.k}(\widetilde{t})\otimes
    -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\otimes
    -^{\widetilde{I_G}}>\longrightarrow ?m_{\widetilde{i}}(\widetilde{t})$
    & $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_{G+P}}$\\
\hline
     &\multicolumn{2}{|p{10cm}|}{\ERIC{Down Message}: Unicast version of (DB): m received
  by a group is forwarded to one specific element $i.k$ of the group}\\
\hline

$(HM)_{\widetilde{k}}$&
$\symb{sv}_{!\widetilde{i}}\triangleq
   $\\
\hline
&\multicolumn{2}{|p{10cm}|}{\ERIC{Horizontal Message}: optimized
  version of Unicast: message m, from a process or a
  gateway, is broadcast to one of its its siblings
  inside the same group}\\

\hline\hline
$(DIS)_{\widetilde{k}}$&
     $\symb{sv}_{u(\widetilde{i}.k)}\triangleq
     <Discard\otimes
     -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\otimes
     -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
         k\}}}>\longrightarrow \tau(DIS)$ &
     $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}$\\
\hline
     &\multicolumn{2}{|p{10cm}|}{\ERIC{DISCARD events} occur in gateways
  under HB protocol, after receiving a broadcast message which
  target address is a sibling of the gateway; this message is
  DISCARDED silently }\\
\hline
$(ERR)_{\widetilde{k}}$&
     $\symb{sv}_{u(\widetilde{i}.k)}\triangleq
     <Error\otimes
     -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\otimes
     -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
         k\}}}>\longrightarrow Error(\widetilde{k})$ &
     $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}$\\
\hline
     &\multicolumn{2}{|p{10cm}|}{\ERIC{ERROR events} may occur in gateways
  in 2 cases: either if the message is targeted to a gateway address,
  that is an error from the emittor (ERR "BadTarget"); or if a gateway
  receives from its parent or brother a message that should not go
  within its subgroup, that is a protocol error (ERR "WrongWay").
  In both cases the ERR message will be transmitted up, for the sake
  of verification }\\
\hline\hline\end{tabular}
\caption{Synchronisation vectors modeling the communication through the HB hierarchy}
\end{figure}

\section{The  Open Transitions of Broadcasting}
% \TODO{Min: to modify the tables. }

%%mofication of Table 1

\begin{figure}[h]
\centerline{ \includegraphics[width=5cm]{XFIG/HB2} }
\caption{(open) pNet structure of Hierarchical Broadcast example}
\label{Fig:simpleHBStruct}
\end{figure}

Figure \ref{Fig:simpleHBStruct} recalls the structure of the pNet tree
for HB example structure, in which gw1, gw2, gw11 are leaves, and P3,
P12, P21, P22, P111 are holes.

The following tables list the open-transition derivable from two of
the first states of the open-automaton of this pNet, including the 2 first
transitions of our scenario, as explained in section \ref{}.

\noindent
\begin{tabular}{|p{2.8cm}|p{9cm}|l|}
\hline\hline
\multicolumn{3}{|l|}{from state $\ostate{000}$}\\
\hline
HB(3) &
\{gw1, gw2\} \{P3\}  \{$a_{gw1}$=$a_{gw2}$=?m(t), $b_{P3}$=!bm(t'), v=$\tau$,[t=t']\} &
$\ostate{110}$\\
\hline
HB(12)&
\{gw11\} \{P12\} \{$a_{gw11}$=?m(t), $b_{P12}$=!bm(t'), v=$\tau$, [t=t' ]\} & $\ostate{001}$\\
\hline
DB&
\{gw1, gw2\}\{\}\{$a_{gw1}$=$a_{gw2}$=?m(t), v=?dm(t'),  [t=t']\}&$\ostate{110}$\\
\hline
UG(1)(UM(12)) &
\{gw1\},  \{P12\} \{$a-{gw1}$=?um(t), $b_{P12}$=!um(t'), v=$\tau$, [t=t']\} &
$\ostate{200}$\\
\hline
UG(2)(UM(k)) ${}^{k \in \{21,22\}}$ &
\{gw2\},  \{Pk\} \{$a_{gw2}$=?um(t), $b_{Pk}$=!um(t'),v=$\tau$, [t=t']\} &
$\ostate{020}$\\
\hline
UG(11)(UM(111)) &
\{gw11\},  \{P111\} \{$a_{gw11}$=?um(t), $b_{P111}$=!m(t),v=$\tau$, [t=t']\} &
$\ostate{002}$\\
\hline\hline
\end{tabular}
\vskip 0.3cm

\NOTE{Eric: one transition of the <020> table, from the draft on my white board}

\noindent
\begin{tabular}{|p{2.8cm}|p{9cm}|l|}
\hline\hline
\multicolumn{3}{|l|}{from state <020>}\\
\hline
HB(2)&
\{gw1,gw2\} \{P3\} \{a1=?m(t), a2=!bm(t'), a3=?m(t'), v=tau, [t=t'=t'' $\land$ isDirRel(t,2)]\} & <100>\\
\hline
HB(12)&
\{gw11\} \{P12\} \{a11=?m(t), a12=!bm(t'),  v=tau, [t=t']\} & <021>\\
\hline
UG(1)(UM(12)) &
\{gw1\},  \{P12\} \{a1=?um(t), a12=!um(t'), v=tau,  [t=t'] \} &
<220>\\
\hline
UG(11)(UM(111)) &
\{gw11\},  \{P111\} \{a11=?um(t), P111=!m(t),v=tau, [t=t']\} &
<022>\\
\hline
ERR(2)&
\{g2\} \{\} \{a2=Error, v=Error2,[t=2]\}&<000>\\
\hline
DiS(2)&
\{g2\} \{\} \{a2=DIS, v=DIS2,[Ancestor(2, t)]\} &
<000>\\
\hline
\hline
\end{tabular}
\vskip 0.3cm

%
%\noindent
%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
%\hline\hline
%\multicolumn{3}{|l|}{from state <1, 1, 0>}\\
%\hline
%HB(12)&
%\{g11\} \{P12\} \{a11=?m(a), a12=!bm(a), v=tau\} & <1, 1, 1>\\
%\hline
%UM(k) ${}^{k \in \{3,12\}}$&
%\{\}\{Pk\}\{ak=!um(a),v=!um(a), isOtherRelative(3, a)\}&<1, 1, 0>\\
%\hline
%UM(1)&
%\{g1\}\{\}\{a1=!um(a),v=!um(a), isOtherRelative(1, a)\}&<0, 1, 0>\\ \hline
%UM(2)&
%\{g2\}\{\}\{a2=!um(a),v=!um(a), isOtherRelative(2, a)\}&<1, 0, 0>\\ \hline
%DG(1)&
%\{g1\}\{SG1\}\{a1=!dm(a),sg1=?dm(a),v=tau\}&<0, 1, 0>\\ \hline
%DG(2)&
%\{g2\}\{SG2\}\{a2=!dm(a),sg2=?dm(a), v=tau\}&<1, 0, 0>\\ \hline
%
%DIS(1)&
%\{g1\} \{\} \{a1=Discard, v=tau\} &
%<0, 1, 0>\\
%\hline
%DIS(2)&
%\{g2\} \{\} \{a2=Discard, v=tau\} &
%<1, 0, 0>\\
%\hline
%ERR(1)&
%\{g1\} \{\} \{a1=Error, v=Error1\}, &
%<0, 1, 0>\\
%\hline
%ERR(2)&
%\{g2\} \{\} \{a2=Error, v=Error2\} &
%<1, 0, 0>\\
%\hline
%UG(11) &
%\{g11\},  \{SG11\} \{a11=?um(a), sg11=!m(a),v=tau, isOtherRelative(11, a)\} &
%<1, 1, 2>\\
%\hline\hline
%\end{tabular}
%\vskip 0.3cm
%\noindent
%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
%\hline\hline
%\multicolumn{3}{|l|}{from state <0, 0, 1>}\\
%\hline
%HB(3) &
%\{g1, g2\} \{P3\} \hfill \{a1=a2=?m(a), a3=!bm(a), v=tau\} &
%<1, 1, 1>\\
%\hline
%DB &
%\{g1, g2\} \{\} \{a1=a2=?m(a), v=?dm(a)\} &
%<1, 1, 1>\\
%\hline
%UG(1) &
%\{g1\},  \{SG1\} \{a1=?um(a), sg1=!m(a),v=tau, isOtherRelative(1, a)\} &
%<2, 0, 1>\\
%\hline
%UG(2) &
%\{g2\},  \{SG2\} \{a2=?um(a), sg2=!m(a),v=tau, isOtherRelative(2, a)\} &
%<0, 2, 1>\\
%\hline
%DG(11)  &
%% $\emptyset$
%\{g11\} \{SG11\} \{a11=!dm(a),sg11=?dm(a) v=tau,\} & <0, 0, 0>\\
%\hline
%
%DIS11 &
%\{g11\},\{\}\{a11=Discard, v=tau \}&<0, 0, 0>\\
% \hline
% ERR11 &
%\{g11\},\{\}\{a11=Error, v=Error11 \}&<0, 0, 0>\\
% \hline\hline
%\end{tabular}
%
%\vskip 0.3cm
%There is the case of Unicast.
%\vskip 0.3cm
%\noindent
%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
%\hline\hline
%\multicolumn{3}{|l|}{from state <0, 0, 0>}\\
%\hline
%DM1 &
%\{g1\} \{P3\}  \{a1=?m(a), a3=!m(a), v=tau, isDirectRelative(1,a)\} &
%<1, 0, 0>\\
%\hline
%DM2 &
%\{g2\} \{P3\}  \{a1=?m(a), a3=!m(a), v=tau, isDirectRelative(2,a)\} &
%<0, 1, 0>\\
%\hline
%DM11 &
%\{g11\} \{P13\}  \{a11=?m(a), a13=!m(a), v=tau, isDirectRelative(11,a)\} &
%<0, 0, 1>\\
%\hline\hline
%\end{tabular}
%\vskip 0.3cm
%\noindent
%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
%\hline\hline
%\multicolumn{3}{|l|}{from state <1, 0, 0>}\\
%\hline
%DG1 &
%\{g1\} \{SG1\}  \{a1=!dm(a), sg1=?dm(a), v=tau, isDirectRelative(1,a)\} &
%<0, 0, 0>\\
%\hline
%UM1 &
%\{g1\} \{\}  \{a1=!um(a), v=!um(a)\} &
%<0, 0, 0>\\
%\hline
%DM2 &
%\{g2\} \{P3\}  \{a1=?m(a), a3=!m(a), v=tau, isDirectRelative(2,a)\} &
%<1, 1, 0>\\
%\hline
%DM11 &
%\{g11\} \{P13\}  \{a11=?m(a), a13=!m(a), v=tau, isDirectRelative(11,a)\} &
%<1, 0, 1>\\
%\hline
%ERR(1)&
%\{g1\} \{\} \{a1=Error, v=tau\} &
%<0, 0, 0>\\
%\hline\hline
%\end{tabular}
%
%\vskip 0.3cm
%
%\noindent
%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
%\hline\hline
%\multicolumn{3}{|l|}{from state <1, 1, 0>}\\
%\hline
%DG1 &
%\{g1\} \{SG1\}  \{a1=!dm(a), sg1=?dm(a), v=tau, isDirectRelative(1,a)\} &
%<0, 1, 0>\\
%\hline
%DG2 &
%\{g2\} \{SG2\}  \{a2=!dm(a), sg2=?dm(a), v=tau, isDirectRelative(2,a)\} &
%<1, 0, 0>\\
%\hline
%UM1 &
%\{g1\} \{\}  \{a1=!um(a), v=!um(a)\} &
%<0, 1, 0>\\
%\hline
%UM2 &
%\{g2\} \{\}  \{a2=!um(a), v=!um(a)\} &
%<1, 0, 0>\\
%\hline
%DM11 &
%\{g11\} \{P13\}  \{a11=?m(a), a13=!m(a), v=tau, isDirectRelative(11,a)\} &
%<1, 1, 1>\\
%\hline
%ERR(1)&
%\{g1\} \{\} \{a1=Error, v=tau\} &
%<0, 1, 0>\\
%\hline
%ERR(2)&
%\{g2\} \{\} \{a2=Error, v=tau\} &
%<1, 0, 0>\\
%\hline\hline
%\end{tabular}

\section{Encapsulating Process arguments}
In Section \ref{section:processSort} we described the Sort of
processes in the holes of the herarchical broadcast architecture.
Here we present a more general solution, using a small pNet as a
filter encapsulating each of the holes. The filter is in
 charge of relabeling the messages
from the process depending on their destination, and filtering the
incoming messages, discarding those received by broadcast, but target
to other processes. This pNet is shown in the following figure:

\centerline{  \includegraphics[width=0.8\linewidth]{ATG/ProcessFilter}}

This solution has the benefit of allowing any process as an argument
fitting the hole, without specific constraints on its sort. The price
is that the pNet structure is a bit more complex, so the open
transitions and open automata will be bigger also. Moreover the filter
has states, and this introduces some additional states and
tau-transitions in the open-automaton.

\section{{pNets Model for Broadcast Flat groups  (BF-pNets):
    definition}\label{sec:bf-pnets-def}}
Given a $HB-\pNet$, we can flatten it to decrease the number of layers
of hierarchical structures using a {\em Flattening Operator}
$\bowtie$.
This operation replaces one or several subgroups in the hierarchical
structure by their content. The corresponding old controllers
(gateways) won't exist after flattening. Fig. \ref{fig:flattening}
shows the flattening operator at work, on 2 subgroups SG1 and SG2, at the
toplevel of the example.
\begin{definition}[Flattening Operation]
Assume a $HB-\pNet$ has the structure:
$\mylangle gw_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}},  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, sg_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}}\myrangle$
where
$ \forall \widetilde{g}\in \widetilde{I_G}$,  the $sg_{\widetilde{g}}$ has the $HB-\pNet$ structure:
 $\mylangle gw_{\widetilde{g}\cdot g_i}^{g_i\in I_{G_{\widetilde{g}}}},  pc_{\widetilde{g}\cdot p_j}^{p_j\in I_{P_{\widetilde{g}}}}, sg_{\widetilde{g}\cdot g_i}^{g_i\in I_{G_{\widetilde{g}}}}\myrangle $.
 \medskip

 Then
the flattening map
$\bowtie_{\widetilde{g}}: HB-pNets\longrightarrow HB-pNets$, where\\

 \medskip
 $\bowtie_{\widetilde{g}}(HB-\pNet)\triangleq \mylangle gw_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g}\}}, gw_{\widetilde{g}\cdot g_i}^{g_i\in I_{G_{\widetilde{g}}}},  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, pc_{\widetilde{g}.\cdot p_j}^{p_j\in I_{P_{\widetilde{g}}}},sg_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g}\}}, sg_{\widetilde{g}\cdot g_i}^{g_i\in I_{G_{\widetilde{g}}}}\myrangle$.
 \medskip

The flattening operator shows one subgroup $sg_{\widetilde{g}}$ can be flatten to one hole of his father group which is linked the gateway $gw_{\widetilde{g}}$, the gateways,the processes ,and the holes of $sg_{\widetilde{g}}$ become the gateways, the processes, and the holes of his father group instead of itself and the gateway that it is linked.

Actually, for any subgroup (hole) of the group, the flattening operation can be done in parallel without the order.
We denote that  $\bowtie_{\widetilde{I_G}}\triangleq\Sigma_{\widetilde{g}\in{\widetilde{I_G}}}\bowtie_{\widetilde{g}}$, where:

 $\bowtie_{\widetilde{I_G}}(HB-\pNet)\triangleq \mylangle  gw_{\widetilde{g}\cdot g_i}^{\widetilde{g}\in \widetilde{I_G}, g_i\in I_{G_{\widetilde{g}}}},  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, pc_{\widetilde{g}\cdot p_j}^{\widetilde{g}\in \widetilde{I_G}, p_j\in I_{P_{\widetilde{g}}}}, sg_{\widetilde{g}\cdot g_i}^{\widetilde{g}\in \widetilde{I_G}, g_i\in I_{G_{\widetilde{g}}}}\myrangle$.
\end{definition}

Especially, if some $\widetilde{g_0}\in{\widetilde{I_G}}$, the $sg_{\widetilde{g_0}}$ has the $HB-\pNet_{\widetilde{g_0}}$ structure: $\mylangle -,  pc_{\widetilde{g_0}\cdot p_j}^{p_j\in I_{P_{\widetilde{g}}}}, -\myrangle$.

 $\bowtie_{\widetilde{g_0}}(HB-\pNet)\triangleq \mylangle gw_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g}\}},   pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, pc_{\widetilde{g_0}\cdot p_j}^{ p_j\in I_{P_{\widetilde{g}}}},sg_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g}\}}\myrangle$.

% If all the subgroups $sg_{\widetilde{g}}$ have the similar structures to $sg_{\widetilde{g_0}}$, $\forall \widetilde{g}\in \widetilde{I_G}$, we have
%
%  $\bowtie_{\widetilde{I_G}}(HB-\pNet)\triangleq \mylangle -,  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, pc_{\widetilde{g}\cdot p_j}^{\widetilde{g}\in \widetilde{I_G}, p_j\in I_{P_{\widetilde{g}}}}, -\myrangle$.

\medskip
%
%\begin{definition}[Equivenlence]
%\NOTE{The equivalence between $HB-\pNet$ and $BF-\pNet$ should be defined.}
%\end{definition}

 Let $HB-\pNet$ node have the structure $\mylangle gw_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}},  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, sg_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}}\myrangle$, with some subgroup the $sg_{\widetilde{g_0}}$ who has the  structure:
 $\mylangle gw_{\widetilde{g_0}\cdot g_i}^{g_i\in I_{G_{\widetilde{g_0}}}},  pc_{\widetilde{g_0}\cdot p_j}^{p_j\in I_{P_{\widetilde{g_0}}}}, sg_{\widetilde{g_0}\cdot g_i}^{g_i\in I_{G_{\widetilde{g_0}}}}\myrangle $, has one corresponding flatten broadcast open $\pNet$ by the flattening operator $\bowtie_{\widetilde{g_0}}$, i.e. $\mylangle gw_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g_0}\}}, gw_{\widetilde{g_0}\cdot g_i}^{g_i\in I_{G_{\widetilde{g}}}},  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, pc_{\widetilde{g_0}.\cdot p_j}^{p_j\in I_{P_{\widetilde{g}}}},sg_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g_0}\}}, sg_{\widetilde{g_0}\cdot g_i}^{g_i\in I_{G_{\widetilde{g}}}}\myrangle$.

\section{Sketch of the proof}
\label{sec:proof-sketch}

In this section we will describe a proof of equivalence between a HB
pNet node (seen as an open pNet), with the corresponding flatten
broadcast open pNet. From this equivalence, it is easy to derive the
equivalence of a fully instantiated (= closed) HB-pNet structure with
the corresponding flatten pNet.

\begin{theorem}
Any $\mathcal{HB-\pNet}$ node is FH-bisimular to the corresponding $\mathcal{BF-\pNet}$ node by the flatting operator $\bowtie$, that is, \\
$\mylangle gw_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}},  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, sg_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g_0}\}},\mylangle gw_{\widetilde{g_0}\cdot g_i}^{g_i\in I_{G_{\widetilde{g_0}}}},  pc_{\widetilde{g_0}\cdot p_j}^{p_j\in I_{P_{\widetilde{g_0}}}}, sg_{\widetilde{g_0}\cdot g_i}^{g_i\in I_{G_{\widetilde{g_0}}}}\myrangle  \myrangle \approx_{FH} \\ \mylangle gw_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g_0}\}}, gw_{\widetilde{g_0}\cdot g_i}^{g_i\in I_{G_{\widetilde{g}}}},  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, pc_{\widetilde{g_0}.\cdot p_j}^{p_j\in I_{P_{\widetilde{g}}}},sg_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g_0}\}}, sg_{\widetilde{g_0}\cdot g_i}^{g_i\in I_{G_{\widetilde{g}}}}\myrangle$.
\end{theorem}

The sketch we give here considers one particular pNet node, with 2
subgroups, and a specific number of processes in each root- and sub-
groups. Also we make some hypotheses on the sorts of the processes.
Clearly the full proof will have to deal with generalisations of this
particular case.

\begin{figure}[h]
\includegraphics[width=6cm]{XFIG/HB2}
\hspace{1cm}
\includegraphics[width=5cm]{XFIG/B2}
\caption{(open) pNet structure of Hierarchical and flat example}
\label{fig:flattening}
\end{figure}

\paragraph{More precisely:}

\paragraph{Principles of the proof:}

We start from the hierarchical pNet, build all its possible behaviours
(building proof trees from possible synch vectors of the pNet, and
possible actions in the sorts of holes), then show that there is a
corresponding behaviour for the flat pNet. Similar method is then
applied in the symetrical direction.

A state of the hierarchical pNet will be a hierarchical vector of
``states'', in which we shall represent the state of a controller with
its name followed by the state index (gateways have only two states,
numered \{0,1\}); and state of holes with simply the name of the hole.
To keep state structure compact and keep readability, we show pLTS
states by their number, subscripted by the name of the gateway. For
processes and sub-groups, that have no states, we only show their name.
%
%
%
%\noindent
%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
%\hline\hline
%\multicolumn{3}{|l|}{from state <0, 0, 0>}\\
%\hline
%Bm(3) &
%\{g1, g2\} \{P3\} \hfill \{a1=a2=?bm(a), a3=!m(a), v=tau\} &
%<1, 1, 0>\\
%\hline
%Bm(12)&
%\{g11\} \{P12,P13\} \{a11=a13=?um(a), a12=!m(a), v=tau\} & <0, 0, 1>\\
%\hline
%Bm(13)&
%\{g11\} \{P12,P13\} \{a11=a12=?um(a), a13=!m(a), v=tau\} & <0, 0, 1>\\
%\hline
%DA &
%\{g1, g2\} \{P3\} \{a1=a2=a3=?bm(a), v=?m(a)\} &
%<1, 1, 0>\\
%\hline
%Um(1) &
%\{g1\},  \{SG1\} \{a1=?bm(a), sg1=!m(a),v=tau, isOtherRelative(1, a)\} &
%<2, 0, 0>\\
%\hline
%Um(2) &
%\{g2\},  \{SG2\} \{a2=?bm(a), sg2=!m(a),v=tau, isOtherRelative(2, a)\} &
%<0, 2, 0>\\
%\hline
%Um(11) &
%\{g11\},  \{SG11\} \{a11=?bm(a), sg11=!m(a),v=tau, isOtherRelative(11, a)\} &
%<0, 0, 2>\\
%\hline
%UA(k) ${}^{k \in \{3,12,13,21\}}$ &
%% $\emptyset$
%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <0, 0, 0>\\
%\hline\hline
%\end{tabular}
%
%\noindent
%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
%\hline\hline
%\multicolumn{3}{|l|}{from state <1, 1, 0>}\\
%\hline
%Bm(12)&
%\{g11\} \{P12,P13\} \{a11=a13=?um(a), a12=!m(a), v=tau\} & <1, 1, 1>\\
%\hline
%Bm(13)&
%\{g11\} \{P12,P13\} \{a11=a12=?um(a), a13=!m(a), v=tau\} & <1, 1, 1>\\
%\hline
%UA(3)&
%\{\}\{P3\}\{a3=!um(a),v=!m(a), isOtherRelative(3, a)\}&<1, 1, 0>\\
%\hline
%UA(1)&
%\{g1\}\{\}\{a1=!um(a),v=!m(a), isOtherRelative(1, a)\}&<0, 1, 0>\\ \hline
%UA(2)&
%\{g2\}\{\}\{a2=!um(a),v=!m(a), isOtherRelative(2, a)\}&<1, 0, 0>\\ \hline
%$Dm_1(DA_1)$ &
%\{g1,g11\}\{SG1,P12,P13\}\{a1=!dm(a), sg1=?m(a),a11=a12=a13=?bm(a), v=tau, isDirectRelative(1,a)\}&<0, 1, 1>\\ \hline
%$Dm_2(DA_2)$ &
%\{g2\}\{SG2,P21\}\{a2=!dm(a), sg2=?m(a), a21=?bm(a), v=tau, isDirectRelative(2,a)\}&<1, 0, 0>\\ \hline
%DISCARD(1)&
%\{g1\} \{\} \{a11DISCARD, v=tau\} &
%<0, 1, 0>\\
%\hline
%DISCARD(2)&
%\{g2\} \{\} \{a2=DISCARD, v=tau\} &
%<1, 0, 0>\\
%\hline
%Um(11) &
%\{g11\},  \{SG11\} \{a11=?bm(a), sg11=!m(a),v=tau, isOtherRelative(11, a)\} &
%<1, 1, 2>\\
%\hline\hline
%\end{tabular}
%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
%\hline\hline
%\multicolumn{3}{|l|}{from state <0, 0, 1>}\\
%\hline
%Bm(3) &
%\{g1, g2\} \{P3\} \hfill \{a1=a2=?bm(a), a3=!m(a), v=tau\} &
%<1, 1, 1>\\
%\hline
%DA &
%\{g1, g2\} \{P3\} \{a1=a2=a3=?bm(a), v=?m(a)\} &
%<1, 1, 1>\\
%\hline
%Um(1) &
%\{g1\},  \{SG1\} \{a1=?bm(a), sg1=!m(a),v=tau, isOtherRelative(1, a)\} &
%<2, 0, 1>\\
%\hline
%Um(2) &
%\{g2\},  \{SG2\} \{a2=?bm(a), sg2=!m(a),v=tau, isOtherRelative(2, a)\} &
%<0, 2, 1>\\
%\hline
%UA(k) ${}^{k \in \{3,12,13,21\}}$ &
%% $\emptyset$
%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <0, 0, 1>\\
%\hline
%UA(11)  &
%% $\emptyset$
%\{g11\} \{\} \{a11=!um(a), v=!m(a)\} & <0, 0, 0>\\
%\hline
%Dm(11)&
%\{g11\},\{SG1\},\{a11=!dm(a),sg11=?m(a), v=tau, isDirectRelative(11,a)\}&<0, 0, 0>\\
%\hline
%DISCARD &
%\{g11\},\{\}\{a11=DISCARD, v=tau, isOtherRelative(11,a) \}&<0, 0, 0>\\ \hline\hline
%\end{tabular}
%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
%\hline\hline
%\multicolumn{3}{|l|}{from state <2, 0, 0>}\\
%\hline
%Bm(12) &
%\{g11\} \{P12,P13\}  \{a11=a12=?bm(a), a13=!m(a), v=tau\} &
%<2, 0, 1>\\
%\hline
%Bm(13) &
%\{g11\} \{P12,P13\}  \{a11=a13=?bm(a), a12=!m(a), v=tau\} &
%<2, 0, 1>\\
%\hline
%Bm(1) &
%\{g1,g2\} \{P3\}  \{a2=a3=?bm(a), a1=!m(a), v=tau\} &
%<0, 1, 0>\\
%\hline
%Um(2) &
%\{g2\},  \{SG2\} \{a2=?bm(a), sg2=!m(a),v=tau, isOtherRelative(2, a)\} &
%<2, 2, 0>\\
%\hline
%UA(k) ${}^{k \in \{3,12,13,21\}}$ &
%% $\emptyset$
%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <2, 0, 0>\\
%\hline
%UA(1)  &
%% $\emptyset$
%\{g1\} \{\} \{a1=!um(a), v=!m(a)\} & <0, 0, 0>\\
%\hline
%Um(11)&
%\{g11\}\{SG11\}\{a11=?um(a), sg11=!m(a), v=tau, isOtherRelative(11,a)\}&<2, 0, 2>\\
%\hline
%DISCARD(1) &
%\{g1\},\{\},\{a1=DISCARD, v=tau, isDirectRelative(1,a)\}&<0, 0, 0>\\
%\hline\hline
%\end{tabular}
%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
%\hline\hline
%\multicolumn{3}{|l|}{from state <0, 2, 0>}\\
%\hline
%Bm(12) &
%\{g11\} \{P12,P13\}  \{a11=a12=?bm(a), a13=!m(a), v=tau\} &
%<0, 2, 1>\\
%\hline
%Bm(13) &
%\{g11\} \{P12,P13\}  \{a11=a13=?bm(a), a12=!m(a), v=tau\} &
%<0, 2, 1>\\
%\hline
%Bm(2) &
%\{g1,g2\} \{P3\}  \{a1=a3=?bm(a), a2=!m(a), v=tau\} &
%<1, 0, 0>\\
%\hline
%Um(1) &
%\{g1\},  \{SG1\} \{a1=?bm(a), sg1=!m(a),v=tau, isOtherRelative(2, a)\} &
%<2, 2, 0>\\
%\hline
%UA(k) ${}^{k \in \{3,12,13\}}$ &
%% $\emptyset$
%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <0, 2, 0>\\
%\hline
%UA(2)  &
%% $\emptyset$
%\{g2\} \{\} \{a2=!um(a), v=!m(a)\} & <0, 0, 0>\\
%\hline
%DISCARD(2)&
%\{g2\},\{\},\{a2=DISCARD, v=tau, isDirectRelative(2,a)\}&<0, 0, 0>\\
%\hline
%Um(11) &
%\{g11\},\{SG11\}\{a11=?um(a), sg11=!m(a), v=tau, isOtherReltive(11, a) \}&<0, 2, 2>\\ \hline\hline
%\end{tabular}
%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
%\hline\hline
%\multicolumn{3}{|l|}{from state <0, 0, 2>}\\
%\hline
%Bm(3) &
%\{g1, g2\} \{P3\} \hfill \{a1=a2=?bm(a), a3=!m(a), v=tau\} &
%<1, 1, 2>\\
%\hline
%DA &
%\{g1, g2\} \{P3\} \{a1=a2=a3=?bm(a), v=?m(a)\} &
%<1, 1, 2>\\
%\hline
%Um(1) &
%\{g1\},  \{SG1\} \{a1=?bm(a), sg1=!m(a),v=tau, isOtherRelative(1, a)\} &
%<2, 0, 2>\\
%\hline
%Um(2) &
%\{g2\},  \{SG2\} \{a2=?bm(a), sg2=!m(a),v=tau, isOtherRelative(2, a)\} &
%<0, 2, 2>\\
%\hline
%UA(k) ${}^{k \in \{3,12,13,21\}}$ &
%% $\emptyset$
%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <0, 0, 2>\\
%\hline
%UA(11)  &
%% $\emptyset$
%\{g11\} \{\} \{a11=!um(a), v=!m(a)\} & <0, 0, 0>\\
%\hline
%Bm(11)&
%\{g11\},\{P12,P13\},\{a11=!m(a),a12=a13=?bm(a), v=tau, \}&<0, 0, 0>\\
%\hline
%DISCARD(11)&
%\{g11\},\{\}\{a11=DISCARD, v=tau, isDirectRelative(11,a) \}&<0, 0, 0>\\ \hline\hline
%\end{tabular}
%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
%\hline\hline
%\multicolumn{3}{|l|}{from state <1, 1, 1>}\\
%\hline
%UA(1)&
%\{g1\}\{\}\{a1=!um(a),v=!m(a), isOtherRelative(1, a)\}&<0, 1, 1>\\
%\hline
%UA(2)&
%\{g2\}\{\}\{a2=!um(a),v=!m(a), isOtherRelative(2, a)\}&<1, 0, 1>\\
%\hline
%UA(3)&
%\{\}\{P3\}\{a3=!um(a),v=!m(a), isOtherRelative(3, a)\}&<1, 1, 1>\\
%\hline
%Dm(11)&
%\{g11\}\{SG11\}\{a11=!dm(a), sg11=?m(a), v=tau, isDirectRelative(11,a)\}&<1, 1, 0>\\ \hline
%$Dm_2(DA_2)$ &
%\{g2\}\{SG2,P21\}\{a2=!dm(a), sg2=?m(a),a21=?bm(a), v=tau, isDirectRelative(2,a)\}&<1, 0, 1>\\ \hline
%DISCARD(1)&
%\{g1\} \{\} \{a1=DISCARD, v=tau, isOtherRelative(1,a)\} &
%<0, 1, 1>\\
%\hline
%DISCARD(2)&
%\{g2\} \{\} \{a2=DISCARD, v=tau, isOtherRelative(2,a)\} &
%<1, 0, 1>\\
%\hline
%DISCARD(11)&
%\{g11\} \{\} \{a11=DISCARD, v=tau, isOtherRelative(11,a)\} &
%<1, 1, 0>\\
%\hline\hline
%\end{tabular}
%\begin{tabular}{|p{2cm}|p{9cm}|l|}
%\hline\hline
%\multicolumn{3}{|l|}{from state <0, 1, 0>}\\
%\hline
%Bm(12) &
%\{g11\} \{P12,P13\}  \{a11=a12=?bm(a), a13=!m(a), v=tau\} &
%<0, 1, 1>\\
%\hline
%Bm(13) &
%\{g11\} \{P12,P13\}  \{a11=a13=?bm(a), a12=!m(a), v=tau\} &
%<0, 1, 1>\\
%\hline
%Um(1) &
%\{g1\},  \{SG1\} \{a1=?um(a), sg1=!m(a),v=tau, isOtherRelative(1, a)\} &
%<2, 1, 0>\\
%\hline
%Um(11) &
%\{g11\},  \{SG11\} \{a11=?um(a), sg1=!m(a),v=tau, isOtherRelative(11, a)\} &
%<0, 1, 2>\\
%\hline
%UA(k) ${}^{k \in \{3,12,13\}}$ &
%% $\emptyset$
%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <0, 1, 0>\\
%\hline
%UA(2)  &
%% $\emptyset$
%\{g2\} \{\} \{a2=!um(a), v=!m(a)\} & <0, 0, 0>\\
%\hline
%$Dm_2(DA_2)$ &
%\{g2\},\{SG2,P21\},\{a2=!dm(a),sg2=?m(a),a21=?bm(a) v=tau, isDirectRelative(2,a)\}&<0, 0, 0>\\
%\hline
%DISCARD(2) &
%\{g2\},\{\}\{a2=DISCARD, v=tau, isOtherRelative(2,a) \}&<0, 0, 0>\\ \hline\hline
%\end{tabular}
%\begin{tabular}{|p{2cm}|p{9cm}|l|}
%\hline\hline
%\multicolumn{3}{|l|}{from state <1, 0, 0>}\\
%\hline
%Bm(12) &
%\{g11\} \{P12,P13\}  \{a11=a12=?bm(a), a13=!m(a), v=tau\} &
%<1, 0, 1>\\
%\hline
%Bm(13) &
%\{g11\} \{P12,P13\}  \{a11=a13=?bm(a), a12=!m(a), v=tau\} &
%<1, 0, 1>\\
%\hline
%DISCARD &
%\{g1\} \{\}  \{a1=DISCARD),  v=tau, isOtherRelative(1,a)\} &
%<0, 0, 0>\\
%\hline
%Um(2) &
%\{g2\},  \{SG2\} \{a2=?bm(a), sg2=!m(a),v=tau, isOtherRelative(2, a)\} &
%<1, 2, 0>\\
%\hline
%Um(11) &
%\{g11\},  \{SG11\} \{a11=?bm(a), sg11=!m(a),v=tau, isOtherRelative(11, a)\} &
%<1, 0, 2>\\
%\hline
%UA(k) ${}^{k \in \{3,21\}}$ &
%% $\emptyset$
%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <1, 0, 0>\\
%\hline
%UA(1)  &
%% $\emptyset$
%\{g1\} \{\} \{a1=!um(a), v=!m(a)\} & <0, 0, 0>\\
%\hline
%$Dm_1(DA_1)$ &
%\{g1,g11\},\{SG1, P12, P13\},\{a1=!dm(a),sg11=?m(a), a11=a12=a13=?bm(a), v=tau, isDirectRelative(1,a)\}&<0, 0, 0>\\
%\hline
%DA(1) &
%\{g11\},\{P12,P13\}\{a11=a12=a13=?bm(a), v=?m(a) \}&<1, 0, 0>\\ \hline\hline
%\end{tabular}
%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
%\hline\hline
%\multicolumn{3}{|l|}{from state <0, 1, 1>}\\
%\hline
%DISCARD(2) &
%\{g2\} \{\}  \{a2=DISCARD),  v=tau, isOtherRelative(2,a)\} &
%<0, 0, 1>\\
%\hline
%DISCARD(11) &
%\{g11\} \{\}  \{a11=DISCARD),  v=tau, isOtherRelative(11,a)\} &
%<0, 1, 0>\\
%\hline
%Um(1) &
%\{g1\},  \{SG1\} \{a1=?um(a), sg1=!m(a),v=tau, isOtherRelative(1, a)\} &
%<2, 1, 1>\\
%\hline
%UA(k) ${}^{k \in \{3,12,13\}}$ &
%% $\emptyset$
%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <0, 1, 1>\\
%\hline
%UA(2)  &
%% $\emptyset$
%\{g2\} \{\} \{a2=!um(a), v=!m(a)\} & <0, 0, 1>\\
%\hline
%$Dm_2(DA_2)$&
%\{g2\},\{SG2,P21\},\{a2=!dm(a),sg2=?m(a),a21=?bm(a), v=tau, isDirectRelative(2,a)\}&<0, 0, 1>\\
%\hline
%Dm(11)&
%\{g11\},\{SG11\},\{a11=!dm(a),sg11=?m(a), v=tau, isDirectRelative(11,a)\}&<0, 1, 0>\\
%\hline\hline
%\end{tabular}
%
%\noindent
%\begin{tabular}{|p{2cm}|p{9cm}|l|}
%\hline\hline
%\multicolumn{3}{|l|}{from state <0>}\\
%\hline
%Bm(3) &
%\{g11\} \{P3,P12,P13,P21\} \hfill \{a11=a12=a13=a21=?bm(a), a3=!m(a), v=tau\} &
%<1>\\
%\hline
%\multicolumn{2}{|l|}{Bm(12,13,21) are similar} & <1>\\
%\hline
%Um(11) &
%\{g11\} \{SG11\} \{a11=?um(a), sg11=!m(a), v=tau\} & <2>\\
%\hline
%DA &
%\{g11\} \{P3,P12,P13,P21\} \{a3=a11=a12=a13=a21=?bm(a), v=?m(a)\} &
%<1>\\
%\hline
%UA(k) ${}^{k \in \{3,12,13,21\}}$ &
%% $\emptyset$
%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <0>\\
%\hline\hline
%\multicolumn{3}{|l|}{from state <1>}\\
%\hline
%DISCARD&
%{g11} \{\} \hfill \{a11=DISCARD, v=tau, isDirectRelative(11,a)\} &
%<0>\\
%\hline
%UA(11)& \{g11\} \{\} \{a11=!um(a), v=!m(a), isOtherRelative(11,a)\}& <0>\\
%\hline
%UA(k) ${}^{k \in \{3,12,13,21\}}$ &
%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <1>\\
%\hline
%Dm(11)& \{g11\} \{SG11\} \{a11=!dm(a), sg11=?dm(a), v=tau, isAncestor(11,a)\} & <0>\\
%\hline\hline
%\multicolumn{3}{|l|}{from state <2>}\\
%\hline
%Bm(11) &
%{g11} \{P3,P12,P13,P21\} \hfill \{a11=!bm(a), a3=a12=a13=a21=?bm(a),
%v=tau, isDirectRelative(11,a)\} & <0>\\
%\hline
%UA(11) &
%{g11} \{\} \hfill \{a11=!um(a),
%v=!m(a), isOtherRelative(11,a)\} & <0>\\
%\hline
%UA(k) ${}^{k \in \{3,12,13,21\}}$ &
%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <2>\\
%\hline
%DISCARD &
%{g11} \{\} \hfill \{a11=DISCARD, v=tau, isAncestor(11,a)\} & <0>\\
%\hline\hline
%
%\end{tabular}

\section{Open-bisimulation is compatible with closed bisimulation ?}

\TODO{Underneath is the rules of the closed semantics. Not sure we
  should keep them here, but we mentionned we should have a proof of
  the relation between the 2 semantics... In an extended version I
  suppose (;-)}

\begin{mathpar}
    \inferrule{\phi,\phi',\phi''\!\in\!\Phi\\s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in J}\rangle} s'\in \to\\\\
      \phi'\!=\!\phi\!+\!\{x'_i\!\to\!V_i|x'_i\!\in\!\iv(\alpha)\land V_i\!\in\!\mathcal{D}\} \\
      e_b\phi'\!=\!\symb{True} \\ \phi''\!=\!\phi'+\{x_j\!\to\! e_j\phi'|j\!\in\! J\}}
    {(s,\phi) \xrightarrow{\alpha\phi'} (s',\phi'') \in\llbracket\mylangle S,s_0,
      \to\myrangle\rrbracket_\Phi}~~{\bf Tr1}
%         \end{mathpar}
% \begin{mathpar}

    \inferrule {\phi,\phi'\in\Phi\\ \alpha_l^{l\in L} \to \alpha \in \overline{\symb{SV}}\\\forall i\in I\phi\setminus
      L\phi.\,s'_i=s_i
      \\ %\iv(\alpha)=(x_k)^{k\in K}\\\\
      \forall l\in L\phi.\,\phi_l\in\Phi\land s_l \xrightarrow{\alpha_l\phi_l} s'_l\in\llbracket\pNet_l\rrbracket_{\Phi}\\\phi'=\phi+\uplus_{l\in L\phi} \phi_{l} }
{\triangleleft s_i^{i\in I\phi}\triangleright \xrightarrow{\alpha\phi'} \triangleleft{s'_i}^{i\in
        I\phi'}\triangleright  \in \llbracket\mylangle \pNet_i^{i\in I},\emptyset,\overline{\symb{SV}}\myrangle\rrbracket_\Phi}~~{\bf Tr2}
\end{mathpar}

\section{Model Checking open-automata}
 \TODO{The following is about the logic formula}

We want to check (and prove) properties on open pNets, using
model-checking techniques on their open-automata. The properties will be
expressed in any version of (action-based) branching temporal logics,
in which we have to add constructs for quantification over the holes
and/or leaves involved in a transition. For simplicity of the
definition, we could choose here ACTL \cite{ACTL1990,ACTL1993} or ACTL*
\cite{DeNicolaVaandrager95}, or the modal $\mu$-calculus
\cite{Koz83}. Instead, for its easiness of
expression of value-passing calculi properties, we use here the {\em
  Model Checking Language} MCL \cite{MateescuFM2008}

\begin{definition}[FH-ACTL ] The logic formula of ACTL (adding  syntax
  for quantifying over open \pNet s : $\forall t\in {\cal{P}}, H_i \xrightarrow{a} H_i^\prime $)
\end{definition}

 \begin{definition}[FH-satisfiability] Suppose that $F$ is an open
   \pNet\ expression, and $\phi$ is a temporal logic formula, we say
   $F$ satisfies the $\phi$, denoted as   $F\vDash_{FH} \phi$,  if
 \end{definition}

 In a quite standard way, we define the model checking problem as
 satisfiability of an FH-ACTL formula in a state of a FH-automaton.
The specificity is that the model (FH-automaton) transitions include
hypotheses about which holes are involved and predicates about their
behaviours.

 \begin{definition}[The Open MC problem]
 \end{definition}

 \section{refinement}
 \begin{definition}[FH-refinement] FH-refinement relation $\ll$ is a
   binary relation in between open \pNet \ expressions iff for any
   open \pNet \ expressions $E$ and $F$, $E\ll F$, we have the
   follows:
 \begin{itemize}
 \item $\P(E)=\P(F)$;
 \item  For any  $E\xrightarrow{S, Pred, a} E'$ based on one open transition $(S, Pred, E')$ for $F$,   there exist a set indexed by $\{j\in J\}$ of transitions  $\{ F\xrightarrow{S_j, Pred_j, a\tau^\star} F_j^\prime| a=a' up\ to\ \alpha-conversation\}$  such that $\forall j\in J, S\subset S_j,  E'\ll F_j'$ and $Pred=\cup_j Pred_j$.
 \end{itemize}
 \end{definition}
 \begin{definition}[Weak FH-refinement] FH-refinement relation $\ll$ is a binary relation in between open \pNet \ expressions iff for any open \pNet \ expressions $E$ and $F$, $E\ll F$, we have the follows:
 \begin{itemize}
 \item $\P(F)=\P(E)$;
 \item  For any  $E\xrightarrow{S, Pred, a} E'$ based on one open transition $(S, Pred, E')$ for $E$,   there exist a set indexed by $\{j\in J\}$ of transitions  $\{ F\xRightarrow{(\uplus_i S_i)_j, (\cap_i Pred_i)_j, \tau^\star a'\tau^\star} F_j^\prime| F\xrightarrow{S_i, Pred_i, a'/\tau} F_i, a=a' up \ to \ \alpha-conversation\}$  such that $\forall j\in J, S=(\uplus_i S_i)_j, E'\ll F_j^\prime$  and $Pred \subseteq \cup_j(\cap_i Pred_i)_j$.
 \end{itemize}
 \end{definition}

 \begin{theorem} Suppose that two \pNet s expressions $E$ and $F$ where $E$ is strong FH-bisimilar to $F$. For any temporal logic formula $\phi$,  if $E\vDash_{FH}\phi$, then we have $F\vDash_{FH} \phi$.
 \end{theorem}

  \section{pNets Model for Hierarchical Broadcast groups  (HB-pNets): definition}\label{sec:b-pnets-def}

In this section, we give the formal model for the broadcast type of
hierarchical groups using our open parameterised networks (pNets).

Hierarchical Broadcast (HB) is a way of implementing broadcasting
algorithms within a large set of processes, with better performances
and scalability. There have been many proposals for hierarchical
broadcast algorithms (cite...), most of them focussing on specific
architectures or features (in particular fault tolerance), and on
performance analysis. Very few have given a formal description of the
algorithm, allowing to reason about their safety properties.

We give here the description of one simple HB algorithm, extracted
from\cite{Taguchi03}, but without fault
tolerance in a first step. For the formal description, we define a
pNet template, that can be used as a building node in a hierarchical
assembly of processes, organised in a tree of sub-groups; communication makes use
of local broadcast within each sub-group, and uses gateways for
transmission of messages, up and down, between the subgroups. The
gateways are described as generic pLTSs, playing the role of
``controllers'' in the pNet node.

\TODO{start with a simple informal description ?}

More precisely, we model a generic structure supporting
  hierarchical groups of processes, including gateways. Then
  we model 3 differents message
  routing algorithms, plus 2 variants, all working on this same
  network topology, namely:
\begin{itemize}
\item Full broadcast: the message goes up to the root of the
  tree, then is broadcasted down to all processes in all groups.
\item Hierarchical broadcast 1: similar to unicast, but within each
  subgroup the communication uses local broadcast. Only the processes
  in the same group than the target process will received the
  message.
This is the algorithm from the original paper \cite{Taguchi03}, in its
simplified version without fault tolerance mechanisms.
\item Hierarchical broadcast 2: same principle, but without horizontal broadcast between sibling processes and gateways: the message has to go up to the enclosing subgroup/gateway, before detecting it can go down to its target.
\item Unicast: the gateways forward the message using the shortest
  route in the tree. The message will reach only the specified target.
\item Unicast 2: same principle, but with detection of sibling situations, and direct sending of messages to sibling gateways/processes, thus shortening the path in a way similar to the Hierarchical Broadcast 1.
\end{itemize}

We will use these 3 algorithms, and their variants, to illustrate the
type of properties we can prove using open pNets and FH-bisimulations.
Note that we cannot hope to get any strong bisimulation equivalences
between them, the intermediate messages introduced by the protocoles
are different. To get interesting properties, we must hide
intermediate messages, and look for weak bisimulation properties.

Here are some examples:

\ERIC{Simple scenario: When hiding everything but send and receive
  messages from processes, the resulting systems with Unicast and
  Hierarchical broadcast are weak equivalent
  ?}

\ERIC{Hierarchical Broadcast Variants: when hiding all horizontal messages
  the two variants are Weak Equivalent ? (same for Unicast variants) }

\ERIC{What kind of relation with Full broadcast ? This is more tricky,
on one hand we have to abstract away from the target id in the
arguments of messages; then full broadcast is indeed broadcasting
everywhere, so the best we can hope is some refinement relation,
because Hierachical Broadcast has naturally less behaviours.}

Given a process configuration, organised hierarchicaly in subgroups,
it is easy to build a pNet tree reflecting the hierarchy, with the
gateways implementing the 3 algorithms. In the next
section, we will prove that this model of the implementation is indeed
equivalent (modulo weak bisimulation) to a flat broadcast.

\medskip

The whole broadcast mechanism of hierarchical groups consists in normal
processes, gateways and subgroups linked by gateways. Normal processes
can send and receive messages to/from the other processes (including
gateways) in the same group, or send up-messages to its enclosing group.

\TODO{Restructure these explanations}
A gateway has external behaviours : it sends down-messages to its associated
subgroup, and receives up-messages from its subgroup.
Gateways behaviour is defined by a simple pLTS with two or three states depending on the algorithm: in the
initial state the gateway can receive a
$?m(\widetilde{tgt})$ message (from its neighbors,
from the enclosing group, or from its own sub-group). Then depending
on the target address
$\widetilde{tgt}$, it will forward the message upward as
$!um(\widetilde{tgt})$, to its corresponding sub-group
as $!dm(\widetilde{tgt})$, or broadcasted to all its
neighbors in the same sub-group  as
$!bm(\widetilde{tgt})$.

\centerline{  \includegraphics[width=\linewidth]{XFIG/SchemaHB+FB}}
\begin{figure}[h]
%
  \caption{Behaviour of a Gateway Broadcast controller }\label{fig:hb-gatewaybroadcast}
\end{figure}

We will describe the behaviour of the gateways in the next section,
for the different algorithms and variants.

\paragraph{Sort of the processes.}
\label{section:processSort}
The process parameters (the holes of the pNet structure) can emit
messages with a target address as an argument (we abstract away from
any other message content), or receive a message, also with the target
address. But because of the Broadcast mechanism, there are two ways a
process can send messages, either horizontally, broadcasted to all its
siblings, denoted $!bm(t)$, or upward to the next hierarchy level,
denoted $!um(t)$. In the appendix, we
will propose a way to implement this mechanism using a small pNet as a
filter. But from now on, this would complexify the examples, so we
simply assume that the processes have a sort $\{?m(t), !bm(t),
!um(t)\}$. A process is always ready to accept an incoming message,
even if the target argument does not match with its own address. The
filter in the appendix will be in charge of discarding misfit messages.

%\begin{figure}[h]
% \centerline{  \includegraphics[width=0.7\linewidth]{XFIG/TreeSchema.JPG}}
%  \caption{Structure of hierarchical groups}\label{fig:tree-schema}
% \end{figure}

% \TODO{ To use ?m instead of ?bm} => done.

%% \centerline{  \includegraphics[width=0.6\linewidth]{ATG/Gateway}}
%%   \caption{Bahaviour of a Gateway controller }\label{fig:hb-gateway}
%%  \end{figure}

%% \paragraph{Variant}
%% Another try, with a different message name for sub-group broadcast, so
%% we do not need to pass the src id along... Not sure it makes a simpler
%% model.

%% \begin{figure}[h]

%% \centerline{  \includegraphics[width=0.8\linewidth]{ATG/Gateway2}}
%%   \caption{Bahaviour of a Gateway HB controller }\label{fig:hb-gateway2}
%%  \end{figure}
%% % \TODO{Eric: to draw the figs of  the broadcast and unicast of
%% % gateway.} done
%% \TODO{Min: to give the formal definition of address and predicates}

%% \begin{figure}[h]
%% \centerline{
%%   \includegraphics[width=0.5\linewidth]{ATG/GatewayUnicast}
%%   \hspace{10mm}
%%   \includegraphics[width=0.4\linewidth]{ATG/GatewayBroadcast}}
%%   \caption{Bahaviour of Unicast and Broadcast gateways}\label{fig:hb-gatewayunicast}
%%  \end{figure}

% \centerline{  \includegraphics[width=0.7\linewidth]{XFIG/TreeSchema.JPG}}

According to the three algorithms mentioned above, we have three kinds of pNet models for Unicast, Full broadcast and Hierarchical broadcast.

\begin{definition}[B-pNets]\label{B-pNets}
A  broadcasting model is a pNet structure : \\
\centerline{
$B-\pNet\triangleq \mylangle gw_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}},  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, sg_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}}, \symb{SV}\myrangle $}
where
\begin{itemize}
\item[$\bullet$] $\widetilde{I_G}$ is the index set over which
  gateways are indexed.  $gw_{\widetilde{g}}^{\widetilde{g}\in
    \widetilde{I_G}}$ is the family of gateways. $\widetilde{I_G}$ is
  also the set over which subgroups are indexed,
  i.e. $gw_{\widetilde{g}}$ links $sg_{\widetilde{g}}$.
   \begin{itemize}
   \item Unicast: $\Sort (gw_{\widetilde{g}})=\{?m_{\widetilde{g}}(\widetilde{tgt}), !um_{\widetilde{g}}(\widetilde{tgt}),!dm_{\widetilde{g}}(\widetilde{tgt}), ERROR_{g}\}$
   \item Flat Broadcast: $\Sort (gw_{\widetilde{g}})=\{?m_{\widetilde{g}}(\widetilde{tgt}), !um_{\widetilde{g}}(\widetilde{tgt}),!dm_{\widetilde{g}}(\widetilde{tgt}), ?um_{\widetilde{g}}(\widetilde{tgt})\}$
   \item Hierarchical Broadcast: $\Sort (gw_{\widetilde{g}})=\{?m_{\widetilde{g}}(\widetilde{tgt}), ?um_{\widetilde{g}}(\widetilde{tgt}), !um_{\widetilde{g}}(\widetilde{tgt}),!dm_{\widetilde{g}}(\widetilde{tgt}), !bm_{\widetilde{g}}(\widetilde{tgt}),DISCARD,
       ERROR_{g}\}$
  \end{itemize}
\item[$\bullet$] $\widetilde{I_P}$ is the index set over which normal
  processes are indexed.
  \item [$\bullet$] $\widetilde{I_{G+P}} \triangleq
    \widetilde{I_G}\uplus\widetilde{I_P}$ is the index set of all
    subnets in a group, i.e. processes and subgroups.
$\widetilde{I_G}$ and $\widetilde{I_P}$ must be \emph{disjoint},
i.e. $\widetilde{I_G}\cap \widetilde{I_P}=\emptyset$. The sort of
$pc_{\widetilde{p}}$ is
\begin{itemize}
\item Unicast: $\Sort(pc_{\widetilde{p}})=\{!m_{\widetilde{p}}(\widetilde{tgt}),
?m_{\widetilde{p}}(\widetilde{tgt})\}$
\item Flat Broadcast: $\Sort(pc_{\widetilde{p}})=\{!m_{\widetilde{p}},
?m_{\widetilde{p}}\}$
\item Hierarchical Broadcast: $\Sort(pc_{\widetilde{p}})=\{!um_{\widetilde{p}}(\widetilde{tgt}),
?m_{\widetilde{p}}(\widetilde{tgt}),
!bm_{\widetilde{p}}(\widetilde{tgt})\}$
\end{itemize}

\item[$\bullet$] The subgroup $sg_{\widetilde{g}}$ can be taken the hole of open pNets which can be inserted the sub-pNets(subgroups) and has the sort: $\Sort (sg_{\widetilde{g}})=\{?m_{\widetilde{g}}(\widetilde{t}), !m_{\widetilde{g}}(\widetilde{t})\}$;

\item[$\bullet$]$\symb{SV}$ is a set of synchronisation vectors. For
  the $HB-\pNet$ node,  we have six kinds of ``normal'' synchronisation
  vectors in the model, plus 2 ``error'' vectors, listed in
  Fig. \ref{fig:HBvectors}.

\end{itemize}
\end{definition}

\centerline{  \includegraphics[width=0.85\linewidth]{ATG/GatewayHB}}

\centerline{
   \includegraphics[width=0.5\linewidth]{ATG/GatewayUnicast}
   \hspace{10mm}
   \includegraphics[width=0.4\linewidth]{ATG/GatewayBroadcast}}

%% \vskip 0.5cm
%% \begin{tabular}{|p{2.2cm}|p{9cm}|l|}
%% \hline\hline
%% \multicolumn{3}{|l|}{Full broadcasting}\\
%% \hline
%% $(UC)_{\widetilde{k}}$ & $
%%      \symb{sv}_{u(\widetilde{i}.k)}\triangleq
%%      <?um_{\widetilde{i}.k}(\widetilde{t})\otimes
%%      -^{\widetilde{I_P}}\otimes
%%      !m_{\widetilde{i}.k}(\widetilde{t})\otimes
%%      -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
%%          k\}}}>\longrightarrow \tau(
%%      m_{\widetilde{i}.k}(\widetilde{t}))$ & $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}$\\
%% \hline
%% $(DM )_{\widetilde{k}}$& $\symb{sv}_{?\widetilde{i}}\triangleq
%%      <?m_{\widetilde{i}.k}(\widetilde{t})\otimes
%%      -^{\widetilde{I_{G+P}}
%%       \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\otimes -^{\widetilde{I_G}}>\longrightarrow
%%      ?m_{\widetilde{i}}(\widetilde{t})$&$\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}\uplus \widetilde{I_P}$\\
%%      \hline
%% $(UM)_{\widetilde{k}}$&
%% $\symb{sv}_{!\widetilde{i}}\triangleq
%%     <!um_{\widetilde{i}.k}(\widetilde{t})\otimes
%%     -^{\widetilde{I_P}\uplus
%%       \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\otimes
%%     -^{\widetilde{I_G}}>\longrightarrow
%%     !m_{\widetilde{i}.k}(\widetilde{t})$ & $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}\uplus \widetilde{I_P}$\\

%% \hline
%% $(DG )$&
%% $\symb{sv}_{?\widetilde{i}}\triangleq
%%      <?m_{\widetilde{i}.k}^{\forall k\in
%%        I_K}(\widetilde{t})\otimes
%%      -^{\widetilde{I_P}}\otimes -^{\widetilde{I_G}}>\longrightarrow
%%      ?m_{\widetilde{i}}(\widetilde{t})$ & $I_K = \{k/\widetilde{i}.k\in \widetilde{I_G}\uplus
%% \widetilde{I_P}\}$\\

%% \hline\hline
%% \end{tabular}
%% \vskip 0.5cm

%% \begin{tabular}{|p{2.2cm}|p{9cm}|l|}
%% \hline\hline
%% \multicolumn{3}{|l|}{Unicast broadcasting}\\
%% \hline
%% $(UC)_{\widetilde{k}}$ & $
%%      \symb{sv}_{u(\widetilde{i}.k)}\triangleq
%%      <?um_{\widetilde{i}.k}(\widetilde{t})\otimes
%%      -^{\widetilde{I_P}}\otimes
%%      !m_{\widetilde{i}.k}(\widetilde{t})\otimes
%%      -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
%%          k\}}}>\longrightarrow \tau(
%%      m_{\widetilde{i}.k}(\widetilde{t}))$ & $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}$\\
%% \hline
%% $(DM )_{\widetilde{k}}$& $\symb{sv}_{?\widetilde{i}}\triangleq
%%      <?m_{\widetilde{i}.k}(\widetilde{t})\otimes
%%      -^{\widetilde{I_P}\uplus
%%       \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\otimes -^{\widetilde{I_G}}>\longrightarrow
%%      ?m_{\widetilde{i}}(\widetilde{t})$&$\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}\uplus \widetilde{I_P}$\\
%%      \hline
%%      $(UM)_{\widetilde{k}}$&
%% $\symb{sv}_{!\widetilde{i}}\triangleq
%%     <!um_{\widetilde{i}.k}(\widetilde{t})\otimes
%%     -^{\widetilde{I_P}\uplus
%%       \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\otimes
%%     -^{\widetilde{I_G}}>\longrightarrow
%%     !m_{\widetilde{i}.k}(\widetilde{t})$ & $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}\uplus \widetilde{I_P}$\\
%% \hline
%% $(DK)_{\widetilde{k}}$&
%% $\symb{sv}_{!\widetilde{i}}\triangleq
%%     <!m_{\widetilde{i}.k}(\widetilde{t})\otimes
%%     ?m_{\widetilde{i}.g}(\widetilde{t})\otimes -^{\widetilde{I_P}\uplus
%%       \widetilde{I_G}\backslash\{\widetilde{i}\cdot k,\widetilde{i}\cdot g\}}\otimes
%%     -^{\widetilde{I_G}}>\longrightarrow
%%     \tau(m_{\widetilde{i}.k}(\widetilde{t}))$ & $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}\uplus \widetilde{I_P}$\\

%% \hline\hline
%% \end{tabular}
%\end{definition}

%
%  \begin{itemize}
%  \item[$(BG)_{\widetilde{k}}$]
%    $\symb{sv}_{b(\widetilde{i}.k)}\triangleq
%    <?m_{\widetilde{i}.j}^{\forall j\in I_K}(\widetilde{t})
%    \otimes !bm_{\widetilde{i}.k}(\widetilde{t})
%    \otimes -^{\widetilde{I_G}}>\longrightarrow \tau( bm(\widetilde{t}))$,
%where $I_K = \{k/\widetilde{i}.k\in \widetilde{I_G}\uplus
%\widetilde{I_P}\}$, and $\widetilde{k}=\widetilde{i}.k$
%
%  \item [$(UM)_{\widetilde{k}}$] $
%    \symb{sv}_{!\widetilde{i}}\triangleq
%    <!um_{\widetilde{i}.k}(\widetilde{t})\otimes
%    -^{\widetilde{I_P}\uplus
%      \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\otimes
%    -^{\widetilde{I_G}}>\longrightarrow
%    !m_{\widetilde{i}.k}(\widetilde{t})$,
%where $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}\uplus \widetilde{I_P}$;
%
%   \item [$(DC)_{\widetilde{k}}$] $
%     \symb{sv}_{d(\widetilde{i}.k)}\triangleq
%     <!dm_{\widetilde{i}.k}(\widetilde{t})\otimes
%     -^{\widetilde{I_P}}\otimes
%     ?m_{\widetilde{i}.k}(\widetilde{t})\otimes
%     -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}}
%     >\longrightarrow
%     \tau(m_{\widetilde{i}.k}(\widetilde{t}))$,
%where $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}$;
%
%   \item [$(UC)_{\widetilde{k}}$] $
%     \symb{sv}_{u(\widetilde{i}.k)}\triangleq
%     <?um_{\widetilde{i}.k}(\widetilde{t})\otimes
%     -^{\widetilde{I_P}}\otimes
%     !m_{\widetilde{i}.k}(\widetilde{t})\otimes
%     -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
%         k\}}}>\longrightarrow \tau(
%     m_{\widetilde{i}.k}(\widetilde{t}))$,
%where $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}$;
%
%   \item [$(DG )$] $\symb{sv}_{?\widetilde{i}}\triangleq
%     <?m_{\widetilde{i}.k}^{\forall k\in
%       I_K}(\widetilde{t})\otimes
%     -^{\widetilde{I_P}}\otimes -^{\widetilde{I_G}}>\longrightarrow
%     ?m_{\widetilde{i}}(\widetilde{t})$,
%where $I_K = \{k/\widetilde{i}.k\in \widetilde{I_G}\uplus
%\widetilde{I_P}\}$.
%
% \item [$(DM )_{\widetilde{k}}$] $\symb{sv}_{?\widetilde{i}}\triangleq
%     <?m_{\widetilde{i}.k}(\widetilde{t})\otimes
%     -^{\widetilde{I_P}\uplus
%      \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\otimes -^{\widetilde{I_G}}>\longrightarrow
%     ?m_{\widetilde{i}}(\widetilde{t})$,
%where $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}\uplus \widetilde{I_P}$;
%
%\item [$(DIS)_{\widetilde{k}}$] $\symb{sv}_{dc}\triangleq
%     <DISCARD_{\widetilde{i}.k}^{\forall k\in
%       I_K}(\widetilde{t})\otimes
%     -^{\widetilde{I_P}}\otimes -^{\widetilde{I_G}}>\longrightarrow
%     \tau(m_{\widetilde{i}.k}(\widetilde{t}))$,
%where $I_K = \{k/\widetilde{i}.k\in \widetilde{I_G}\uplus
%\widetilde{I_P}\}$.
%\end{itemize}
%\end{itemize}

\medskip

   \begin{example}
We sketch here one example showing how to send one message from one
process in one group to the other process in the other group by using
broadcast mechanism of Hierarchical groups in {\sl HB-pNets}. Here we
use 12, 122,... instead of the denotation above 1.2 , 1.2.2,... in the
definition for short.
   \end{example}

\begin{figure}[h]
  \includegraphics[width=1.0\linewidth]{ATG/Inst5}
  \caption{A Hierarchical Broadcast pNet Structure }\label{fig:hb-structure}
 \end{figure}

In Fig.~\ref{fig:hb-structure}, suppose that one root group $G$ has
  two gateways $g_1$ and $g_2$ which link two subgroups $G_1$ and
  $G_2$, and a normal process $P_3$. Subgroup $G_1$ has one gateway $g_{12}$ which links the
  subsubgroup $G_{12}$ one normal process $P_{12}$.
  $G_2$ and $G_{11}$ have two normal processes respectively.

The procedure of sending one message from process $P_{21}$ to process
$P_{122}$ can be described as follows:

\TODO{To be written, unless it is already in a previous section ?}

\section{Computing the open operational semantics}

In this section we show how to unfold the operational semantic rules
on our hierarchical broadcast example, compute open transitions, and
start building the open automaton.

The sketch we give here considers one particular pNet node, with 2
subgroups, and a specific number of processes in each root- and sub-
groups. Also we make some hypotheses on the sorts of the processes.
Clearly the full proof will have to deal with generalisations of this
particular case.

% \newcommand{\NetS}[1]{\symb{\guillemotleft} #1 \symb{\guillemotright}}

%% A transition in the proof tree is either :
%% \begin{itemize}
%% \item a transition in a pLTS, with eventually a state change.
%% \item an action in the sort of a Hole.
%% \item the ``global action'' resulting from a synchronisation vector in the pNet.
%% \end{itemize}

%% \begin{figure}[h]
%% $\NetS{0_{g1}, 0_{g2}, \sm{P3}, \NetS{0_{g11}, \sm{P12}, \sm{P13},
%%       \sm{SG11}}, \NetS{\sm{P21}, \sm{P22}}}$
%% \hfill
%% $<<0_{g1}, 0_{g2}, 0_{g11}>>$

%% \caption{initial state of our example, and state of the corresponding Expr}
%% \end{figure}

For each possible synch vector of the root node, we build a proof
tree. From each such proof tree we derive a {\em open transition},
representing a symbolic transition in the open automaton
of the pNet.
%% Now we compute the corresponding open-transition, getting rid of the
%% intermediate deduction steps, keeping only premisses for the pLTS
%% and holes involved, and the predicate.

%% \begin{mathpar}
%%   \inferrule
%%       {0_{gw2} \xrightarrow{a_{gw2}} 2_{gw2} \\
%%            \xrightarrow{b_{P21}}
%%            \\ Pred_{Root}
%%       }
%%            {\ostate{000} \xrightarrow{v} \ostate{020}}
%%       ~~ [UG\_2(UM\_21)]
%% \end{mathpar}

\medskip
Following the residual algorithm from section \ref{sec:xxx}, we can
build the full open-automaton of our pNet. We give here in Figure
\ref{fig:xxx} only a small view of its first two states.

\paragraph{Proving equivalences}

We present a (partial) set of transitions of our two processes in the
following tables. For each state of the expression, we have a set of
lines, each defining one open transition starting from this state.
For each specific+ation rule, we show the vectors used to prove it, the
formal hypothesis and the predicte, and the resulting expression
state.

The resulting LTS for our example is shown in Fig. \ref{fig:HB-lts}.

\begin{figure}[h]
\includegraphics[width=9cm]{ATG/FullLTS}

\caption{(symbolic) behaviour of the example, Hierarchical version}
\label{fig:HB-lts}
\end{figure}

For the flattened version, the computation of the symbolic graph is similar, but of course simpler. The result is shown in Fig. \ref{fig:Flat-lts}.

\begin{figure}[h]
\includegraphics[width=9cm]{ATG/FlatLTS}

\caption{(symbolic) behaviour of the example, Flat version}
\label{fig:Flat-lts}
\end{figure}

%%% REVISION: what we did:
%%% added the notation (x|-> J) page 3 (used to define composition)
%%% defined pnet composiiton (filling a hole)
%%% defined pnests bisimilarity (trivial)
%%% added constraint on synchronisation vector: no fresh variable in target action
%%% changed Pred def: iff instead of implies

### 2017-02-02 2017-Xudong-SMT/OpenPNets-SMT.tex
premier jet...

--- 2017-02-01 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 \newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
-\newcommand{\LUDO}[1]{\textcolor{green}{#1}}
 \newcommand{\coloncolon}{{:\hspace{-.2ex}:}}
@@
 
-\title{More equivalences for Open pNets\thanks{This work was partially 
+\title{Using SMT engine to generate Symbolic Automata\thanks{This work was partially 
 funded by the Associated Team FM4CPS
   between INRIA and ECNU, Shanghai}}
-\author{ Ludovic Henrio\inst{1}  \ \ \  Eric Madelaine\inst{1,2} \ \ \ Min Zhang\inst{3}}
+\author{ Xudong Qin\inst{3}  \ \ \  Eric Madelaine\inst{1,2}} 
 \institute{Univ. of Nice Sophia Antipolis, CNRS, UMR 7271, 06900 Sophia Antipolis, France
@@
 \begin{abstract}
-  Strong bisimulation allows to compare open systems described using the pNets model.
-  In practice, as happens in process algebras, it is too strong, and
-  we need to define some coarser relations, taking into account
-  invisible or internal moves.
-
-  Open pNets have a notion of \emph{synchronised actions}
-  generalizing the usual internal actions (e.g. $\tau$ of CCS, or $i$
-  in Lotos).
-
-  We use this notion to define an equivalence relation similar to
-  the classical \emph{weak bisimulation}, and study its properties...
-
-  refinement preorders ?
-
-  Algorithms ?
-
-  Which significant (small) use-case ?
+  We implement the symbolic semantics of open pNets using their
+  so-called ``Open Automaton'' behavioural semantics. This involve
+  building predicates expressing the synchronisation conditions
+  allowing some combination of events in the pNet system. These
+  predicates are typically built using first order logic, plus some
+  predicates specific of particular action algebras. To reduce the
+  complexity of the generated open automata, we use the Z3 SMT engine
+  to check satisfiability of the predicates, and prune the state
+  space..
 
@@
 
-\ERIC{imported from FORTE'16, but many of these works also had weak
-  version... we need to have another look}
+\ERIC{imported from FORTE'16, }
 
@@
 
+\paragraph{Context}
+\TODO{
+  Summary of previous works on pNets and open pNets => 1/2 page.\\
+  Longterm goals:\\
+  - open pNets to represent operators and program skeletons (ref to
+  \cite{PDP2015})\\
+  - compute semantics in term of open transitions\\
+  - compute equivalence (bisimulation of open automata)\\
+  - model-check properties of open systems
+  }
 \paragraph{Contribution}
@@
 \paragraph{Structure.}
+
+\section{Running Example(s)}
 
@@
 
-% \TODO{Check whether we really use all these notations}
-
 \paragraph*{Term algebra.}
@@
 set of state modifications.
-%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
-%different 
-%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
+
 \begin{definition}[Open transitions]
@@
 
-	%% \TODO{ We should be careful here: after (re) reading "Huimin
-	%% 	Lin, 'Symbolic Transition Systems with Assignements', Concur'96" I
-	%% 	think handling assignments is not trivial, even for comparisons of pLTSs. }
-
 	The rule for a pLTS $p$  checks that the guard 
@@
 	\medskip
-%        \TODO{may be explain how $\Pred(SV,a_i^{i\in I_k},b_j^{j\in
-%            J_k},v)$ is built ? You mean more than what is written on previous page????}
-	%%    \TODO{I have tentatively added the sort constraint on hole actions, that was
-	%%not included in the first version... I'm unsure whether this is the best place to
-	%%include it, because it may change the decidability conditions on predicates}
 
@@
 \subsection{Computing and using open automata}
-In this section we present a simple algorithm to construct the open
+In this section we present an algorithm to construct the open
 automaton representing the behaviour of an open pNet, and we prove that
@@
 
-\TODO{Eric: refine the algorithm description}
+\TODO{Refine the algorithm description}
 
@@
 
-\section{Tooling}
-
-\TODO{Eric: high level description of the implementation}
+\section{Implementation}
+
+\TODO{Xudong: Detailed description of the implementation}
 
@@
 \\
-=> Variable names are generated for all ``fresh'' and ``clone'' operations, using structured variable names ensuring uniqueness of fresh names, but also reasonable readability of these names for debugging purposes.\\
+=> Variable names are generated for all ``fresh'' and ``clone''
+operations, using structured variable names ensuring uniqueness of
+fresh names, but also reasonable readability of these names for
+debugging purposes.\\
+=> Assignements\\
 => Satisfiability check is done only at toplevel of the deduction tree construction.
@@
 
-\TODO{Eric: full result of the tool execution on the running example}
-
-\section{Bisimulation}
-\label{section:bisimulation}
-
-	Now we use our symbolic operational semantics to define a notion of
-	strong (symbolic) bisimulation. Moreover this equivalence is decidable whenever we 
-	have some
-	decision procedure on the predicates of the action algebra.
-
-%% , that we prove compatible with the
-%% composition of open pNets. \TODO{do we really know this ?}
-
-The equivalence we need is a strong bisimulation between
-pNets having exactly the same Holes with the same sorts, but using a
-flexible matching 
-between open transition, to accommodate comparisons between pNet
-expressions with different architectures.
- We name it FH-bisimulation,
- as a short cut for the ``Formal Hypotheses'' manipulated in the
- transitions, but also as a reference to the work of De Simone~\cite{deSimone85},
- that pioneered this idea. Formally:
-
- \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim}
-
-\noindent
-\begin{minipage}{0.69\linewidth} 	Suppose that
-   $A_1 = <L_1,J,\mathcal{S}_1, s^1_0,
-   \mathcal{T}_1>$ and $A_2 = <L_2,J,\mathcal{S}_2,s^2_0, \mathcal{T}_2>$
-   are open automata where the set
-   of holes are equal %\LUDO{added:} 
-   and of the same sort.  %\LUDO{changed:} 
-      Let 
-      \ERIC{$\mathcal{R}=\{(s^1,s^2|\Pred_{s^1,s^2})\}$} be a
-      relation over the sets 
-      $\mathcal{S}_1$ and $\mathcal{S}_2$ 
-      constrained by a predicate.  More precisely, for any pair $(s^1,s^2)$, there is a 
-      single
-      $(s^1,s^2|\Pred_{s^1,s^2})\in\mathcal{R}$  stating that $s^1$ and $s^2$ are related if $\Pred_{s^1,s^2}$\ 
-      is 
-      true.
-\end{minipage}
-\hspace{2mm}
-\begin{minipage}{0.30\linewidth}
-	\includegraphics[width=\linewidth]{XFIG/Bisim}
-\end{minipage}
- Then 
-   $\mathcal{R}$ is an FH-bisimulation iff for any  states
-   $s^1\in\mathcal{S}_1$ and\\ $s^2\in\mathcal{S}_2$, $(s^1,s^2|\Pred)\in\mathcal{R}$, we 
-   have
-   the following:
-
- \begin{itemize}
- \item  For any open transition $OT$ in $\mathcal{T}_1$:
- \begin{mathpar}
-     \inferrule*[myfraction=\reddottedrule]
-         {\{s^1_i\xrightarrow{a_i}_i s^{1'}_i\}^{i\in I_1}, % , s^1_i,s^{1'}_i\in 
-         %States(I_1)
-           \{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
-         {s^1 \xrightarrow {v} s^{1'}}
-
-\end{mathpar}
- there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
- \begin{mathpar}
-%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
-    \inferrule*[myfraction=\reddottedrule]
-         {\{s^{2}_i\xrightarrow{a_{i x}}_i s^{2}_{i x}\}^{i\in I_{2 x}},
-           \{\xrightarrow{b_{j x}}_j\}^{j\in J_{2x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {s^2 \xrightarrow {v_x} s^{2}_x}
-%         \right)
-\end{mathpar}
- such that  $\forall x, J_1=J_{2x}, (s^{1'},s^{2}_x|\Pred_{s^{1'},s^{2}_x})\in 
- \mathcal{R}$; 
- and  \\
- $\Pred \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-   \left( \forall j. b_j=b_{jx}  \Rightarrow \Pred_{OT_x}
-     \land v\!=\!v_x \land  
-     \Pred_{s^{1'},s^{2}_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
-     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
-     %     \right)$.
-
- \item  and symmetrically any open transition from $s^2$ in $\mathcal{T}_2$ can be 
-      covered by a set of transitions from $t^1$ in $\mathcal{T}_1$.
- \end{itemize}
-
- \TODO{Eric: il reste des petits bugs genre $s^{2'}_x$ plutot que
-   $s^{2}_x$}
-
-%Where $\symb{Subst}(\Pred,\Post)$ is the parallel substitution of all
-%assigned variables.
-Two pNets are FH-bisimilar if there exist a relation between their associated 
-automata that is an FH-bisimulation and their initial states are equivalent.
-
- \end{definition}
-Classically, $\Pred_{target_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}$
-applies in parallel the  
-substitutions $\Post_{OT}$ and $\Post_{OT_x}$ (parallelism is crucial
-inside each $\Post$ set but $\Post_{OT}$ is independent from
-$\Post_{OT_x}$), applying the assignments of the involved rules.
-
-\medskip
-\ERIC{If we assume that everything is finite (states and transitions in the
-open automata, and the predicates in $\mathcal{R}$, then it is easy to
-prove that it is decidable whether a relation is a 
-FH-bisimulation provided the logic of the predicates is decidable (see
-\cite{Forte2016}). }
-
-\begin{theorem}[Decidability of FH-bisimulation]
-Let $A_1$ and $A_2$ be finite open automata
-and $\mathcal{R}$ a relation over their states $\mathcal{S}_1$ and
-$\mathcal{S}_2$ constrained by a finite set of predicates. Assume that
-the predicates inclusion is decidable over  
-the action algebra $\mathcal{A}_P$. Then it is decidable whether the relation 
-$\mathcal{R}$ is a FH-bisimulation.
-
-\end{theorem}
-
-\section{Composability}
-
-The main interest of our symbolic approach is to define a method to
-prove properties directly on open structures, that will be preserved
-by any correct instantiation of the holes. In this section we define a
-composition operator for open pNets, and we prove that it preserves
-FH-bisimulation. More precisely, one can define two preservation
-properties, namely 1) when one hole of a pNet is filled by two bisimilar
-other (open) pNets; and 2) when the same hole in two bisimilar pNets are
-filled by the same pNet, in other words, composing a pNet with two
-bisimilar contexts. The general case will be obtained by
-transitivity of the bisimulation relation. We concentrate here on the
-second property, that is the most interesting.
-
-\begin{theorem}[FH-Bisimulation is an equivalence]\label{thm-equiv} Suppose $\mathcal{R}$ 
-is an FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
-reflexive, symmetric and transitive.
-
-\end{theorem}
-
-\begin{definition}[pNet composition]
-	An open pNet: $\pNet = \mylangle \pNet_i^{i\in I}, S_j^{j\in J}, 
-	\overline{\symb{SV}}\myrangle$
- can be (partially) filled by providing  a pNets $\pNet'$ of the
-	right sort to fill one of  its holes.	
-	Suppose $j_0\in J$:
-	%% \[\mylangle \pNet_i^{i\in I},S_j^{j\in J}, \symb{SV}_k^{k\in
-	%%   K}\myrangle\left[(\pNet'_i)^{i\in L}\right]= \mylangle \pNet_i^{i\in
-	%%   I}\left[(\pNet'_i)^{i\in L}\right]\uplus(\pNet'_i)^{i\in J\cap L},S_j^{j\in 
-	%%J\setminus L},
-	%% \symb{SV}_k^{k\in K}\myrangle
-	%% \]
-	\[\pNet\left[\pNet'\right]_{j_0}= \mylangle 
-	\pNet_i^{i\in I}\uplus\{j_0\mapsto \pNet'\},S_j^{j\in J\setminus \{j_0\}},
-	\overline{\symb{SV}}\myrangle
-	\]
-\end{definition}
-
-\LUDO{added congruence theorem below}
-\begin{theorem}[Congruence]\label{thm-congr-eq}
-	Consider an open pNet:
-	$\pNet = \mylangle \pNet_i^{i\in I}, S_j^{j\in J}, 
-	\overline{\symb{SV}}\myrangle$.
-	Let $j_0\in J$ be a hole. Let $Q$ and $Q'$ be two FH-bisimilar pNets such that 
-	$\Sort(Q)=\Sort(Q')=S_{j_0}$\footnote{Note that $\Sort(Q)=\Sort(Q')$ is ensured by 
-	stronfg bisimilarity.}. Then 
-	$\pNet[Q]_{j_0}$ and 
-	$\pNet[Q']_{j_0}$ are FH-bisimilar.
-\end{theorem}
-
-\begin{theorem}[Context equivalence]\label{thm-ctxt-eq}
-	Consider two FH-bisimilar open pNets:
-	$\pNet = \mylangle \pNet_i^{i\in I}, S_j^{j\in J}, 
-	\overline{\symb{SV}}\myrangle$ and 	$\pNet' = \mylangle {\pNet'}_i^{i\in I}, 
-	S_j^{j\in 
-	J}, 	\overline{\symb{SV'}}\myrangle$ 
-	(recall they must have the same holes to be bisimilar).
-	Let $j_0\in J$ be a hole, and $Q$ be a pNet such that $\Sort(Q)=S_{j_0}$. Then $\pNet[Q]_{j_0}$ and 
-	$\pNet'[Q]_{j_0}$ are FH-bisimilar.
-\end{theorem}
-
-Finally, the previous theorems can be composed to state a general theorem about 
-composability and FH-bisimilarity.
-\begin{corollary}[Composability]
-	Consider two FH-bisimilar pNets with an arbitrary number of holes, when replacing, 
-	inside those two original pNets, a subset of the holes by FH-bisimilar pNets, we 
-	obtain two FH-bisimilar pNets.
-\end{corollary}
-%
-%In the following we use $\approx$ to denote equality modulo alpha conversion of free 
-%variables. In practice, $x\approx y$ can be obtained if: $x=clone(a) \land y=clone(a)$.
-
-\section{Weak bisimulation}
-
-Weak symbolic bisimulation was introduced to relate transition systems
-that have indistinguishable behaviour, with respect to some definition
-of \emph{invisible actions} that are considered internal to some
-subsystem, and consequently cannot be observed, nor used for
-synchronisation with their context.
-As the notions of invisible action varies in different contexts,
-e.g. $tau$ in CCS, and $i$ in Lotos, we will rely here on some set of
-\emph{invisible actions} depending on a specific action algebra.
-
-\TODO{we should understand if it make sense to distinguish invisible
-  from synchronised actions: in the Forte paper we wrote ``using  as 
-\emph{invisible actions} a subset of the
-\emph{synchronised actions} defined in Section~\ref{section:pnets}''}.
-
-%% Proving bisimulation properties on our hierarchical broadcast example
-%% would take too much space for this paper. Moreover, interesting
-%% properties of the HB example would rather be adequate for weak
-%% bisimulation, and its large state-space would require some
-%% tool-assistance, both for the generation of the open-automata and for
-%% their comparison.
-
-Classicaly, we start by defining a derived transition relation based
-on sequences of invisible actions:
-
-\begin{definition}[Weak open transitions]
-  Let $A = <L,J,\mathcal{S},s_0,\mathcal{T}>$ be an open automaton.
-  We define $\mathcal{T^*}$ the \emph{Weak open transition relation}
-  with respect to a set of invisible actions $\mathcal{Inv}$ as:
-
- \begin{mathpar}
- \inferrule*[myfraction=\reddottedrule]
-         {\{s_i\xrightarrow{a_i}_i s'_i\}^{i\in I_1}, 
-           \{\xrightarrow{b_j}_j\}^{j\in J},\Pred,\Post}
-         {s \xRightarrow {v} s'}
-         \in \mathcal{T}^*
- \end{mathpar}
-
- iff there exists a sequence of open transitions
-         $OT_x^{x\in X} \subseteq \mathcal{T}$ such that:
-
- \TODO{Pas si simple !!!}
-
- \end{definition}
-
-\begin{definition}[Weak FH-bisimulation]\label{def-Weak-bisim}
-
-\noindent
-Let $A_1$ and $A_2$ be open automata, and $mathcal{R}$ a relation over
-$S_1$ and $S_2$, as in Definition \ref{def-FH-bisim}.
-
-Then 
-   $\mathcal{R}$ is an Weak FH-bisimulation iff for any  states
-$s^1\in\mathcal{S}_1$ and\\
-$s^2\in\mathcal{S}_2$, $(s^1,s^2|\Pred)\in\mathcal{R}$, we 
-   have the following:
-
- \begin{itemize}
- \item  For any open transition $OT$ in $\mathcal{T}_1$:
- \begin{mathpar}
-     \inferrule*[myfraction=\reddottedrule]
-         {\{s^1_i\xrightarrow{a_i}_i s^{1'}_i\}^{i\in I_1},
-           \{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
-         {s^1 \xrightarrow {v} s^{1'}}
-
-\end{mathpar}
- there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2^*$:
- \begin{mathpar}
-    \inferrule*[myfraction=\reddottedrule]
-         {\{s^{2}_i\xrightarrow{a_{i x}}_i s^{2}_{i x}\}^{i\in I_{2 x}},
-           \{\xrightarrow{b_{j x}}_j\}^{j\in J_{2x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {s^2 \xRightarrow {v_x} s^{2'}_x}
-\end{mathpar}
- such that  $\forall x, J_1=J_{2x}, (s^{1'},s^{2'}_x|\Pred_{s^{1'},s^{2'}_x})\in \mathcal{R}$; 
- and  \\
- $\Pred \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-   \left( \forall j. b_j=b_{jx}  \Rightarrow \Pred_{OT_x}
-     \land v\!=\!v_x \land  
-     \Pred_{s^{1'},s^{2'}_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
-
- \item  and symmetrically any open transition from $s^2$ in $\mathcal{T}_2$ can be 
-      covered by a set of weak transitions from $t^1$ in $\mathcal{T}_1^*$.
- \end{itemize}
-
-Two pNets are Weak FH-bisimilar if there exist a relation between their associated 
-automata that is an Weak FH-bisimulation and their initial sstates are equivalent.
-
- \end{definition}
-
-\TODO{Here we should include:
-  \\  - A definition for Weak FH-Bisimulation
-  \\  - A sufficient condition for an open PNet to preserve Weak-FH,
-  including: 1) no non-deterministic Tau-choice in the pLTSs, 2) a
-  synch vector propagating Tau from a subnet $pNet_i$ mandatory
-  everytime $pNet_i$ can do some visible action in the current
-  context, 3) if we have a vector <Tau, -, a, - > --> b with ``a'' a visible
-  action of some CLOSED subnet, then b=Tau. 
-  \\  - the corresponding Congruence theorem
-  \\- An example
-}
-
-\TODO{Eric: ask Elie, Hubert or others about interesting weak
-  equationnal theories for Lotos -- DONE, waiting for answer...}
-
-\TODO{Ludo: ask Simon for weak properties of Bip composition
-  ``operators'' -- DONE!}
+\TODO{Xudong: full result of the tool execution on the running example}
 
@@
 
-We are currently extending this work,  looking at  both further properties of 
-FH-bisimulation, but also
-the relations with existing equivalences on closed systems.
-We also plan to apply open pNets to the study of complex composition
-operators in a symbolic way, for example in the area of parallel
-skeletons, or distributed algorithms.
-We have started developping some tool support for computing the
-symbolic semantics in term of open-automata. The following steps will
-be the development of algorithms and tools for checking 
-FH-bisimulations, and interfacing with decision engines for
-predicates, typically SMT solvers. Those tools will include
-an algorithm that partitions the states and generates the right
-conditions (automatically or with user input) for checking
-whether two open pNets are bisimilar.
-
-Independently, it is clear that most interesting properties of
-such complex systems will not be provable by strong bisimulation.
-Next steps will include the investigation of weak
-versions of the FH-bisimulation, using the notion of
-\emph{synchronised actions} mentionned in the paper.
-%We are convinced that this work will contribute to the design of tools for
-%verifying open distributed systems.
-
 \bibliographystyle{lncs/splncs}
@@
 
-\newpage
-\appendix
-
-\section{Proof of associativity of Enable pNet.}
-\label{appendix:assoc}
-
-Using the usual encoding of the Lotos Enable operator (see
-Fig. \ref{schema:enable-pnets}), we build now open automata for two  
-open pNets \texttt{P>>(Q>>R)} and \texttt{(P>>Q)>>R)}, and 
-prove their bisimilarity.
-\begin{figure}[t]
-\centerline{ % \includegraphics[width=0.5\linewidth]{XFIG/Struct-P-QR}
-% \includegraphics[width=0.35\linewidth]{XFIG/Struct-PQ-R}}
-  \includegraphics[width=0.60\linewidth]{XFIG/P-QR}
-  \hspace{5mm}
- \includegraphics[width=0.27\linewidth]{XFIG/PQ-R}}
-  \caption{Structure of the pNets for ``P>>(Q>>R) and (P>>Q)>>R''}
-  \label{schema:enable-assoc}
-\end{figure}
-
-The two open pNets are drawn in Fig. \ref{schema:enable-assoc}. To
-alleviate the drawing, we have only 
-  given one instance (C2) of the enable controller pLTSs, and one example of
-  the set of synchronisation vectors.
-
-  Below we give the two open automata for these pNets. In the
-  open-transitions in these 
-    automata, the predicates are very simple, and for readability
-    we show them directly in the transitions.
-    Remark that while the structure of the automaton states is useful
-    for their construction, it is not relevant later, so we have
-    dropped this structure when drawing the automaton.
-
-\begin{figure}[h]
-  \begin{minipage}{2cm}
-  \includegraphics[width=\linewidth]{XFIG/PQR-automaton}
-  \end{minipage}
-  \hspace{10mm}
-  \begin{minipage}{7cm}
-  \begin{eqnarray*}
-    OT_1 & = \openrule{0 \xrightarrow{l}_{C_3} 0
-    	\\\xrightarrow{a1}_P\\ a1\neq\delta(x)}
-    {\ostate{00} \xrightarrow{a1} \ostate{00}}\\
-    OT_2 & = \openrule{
-                       0 \xrightarrow{\delta}_{C_3} 1, ~~
-                            0 \xrightarrow{l}_{C_4} 0,  ~~                 
-                            \{\xrightarrow{\delta(x1)}_P, ~~
-                            \xrightarrow{acc(x1)}_Q\}
-                      }
-                      {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}    \\
-    OT_3 & = \openrule{0 \xrightarrow{l}_{C_4} 0,
-                        \\1 \xrightarrow{r}_{C_3} 1,\\
-                        \xrightarrow{a2}_Q,\\a2\neq\delta(x)
-                        }
-    {\ostate{10} \xrightarrow{a2} \ostate{10}}\\
-    OT_4 & = \openrule{
-                       0 \xrightarrow{\delta}_{C_4} 1, \qquad
-                       1 \xrightarrow{r}_{C_3} 1, \qquad
-                       \{\xrightarrow{\delta(x2)}_Q, \qquad 
-                       \xrightarrow{acc(x2)}_R\} 
-                       }
-                      {\ostate{10} \xrightarrow{\underline{\delta(x2)}} \ostate{11}}    \\
-    OT_5 & = \openrule{1 \xrightarrow{r}_{C_3} 1, \\1 \xrightarrow{r}_{C_4} 1, 
-    	\\\xrightarrow{a3}_R
-    	}
-    {\ostate{11} \xrightarrow{a3} \ostate{11}}
-    \end{eqnarray*}
-  \end{minipage}
-  \caption{Open Automaton for the term ``P>>(Q>>R)''}
-  \label{schema:enable3bis}
-\end{figure}
-
-\begin{figure}[t]
-  \begin{minipage}{2cm}
-  \includegraphics[width=\linewidth]{XFIG/PQR2-automaton}
-  \end{minipage}
-  \hspace{10mm}
-  \begin{minipage}{7cm}
-  \begin{eqnarray*}
-    OT'_1 & = \openrule
-             {
-               0 \xrightarrow{l}_{C_3} 0,~~0 \xrightarrow{l}_{C_4} 0,~~
-               \{\xrightarrow{b1}_P\},~~ b1\neq\delta(y)
-               }
-             {\ostate{00} \xrightarrow{b1} \ostate{00}}\\
-    OT'_2 & = \openrule
-             {
-                       0 \xrightarrow{l}_{C_5} 0, ~~
-                       0 \xrightarrow{\delta}_{C_6} 1,  ~~
-              \{\xrightarrow{\delta(y1)}_P,~~      \xrightarrow{acc(y1)}_Q\}~~ 
-                      }
-             {\ostate{00} \xrightarrow{\underline{\delta(y1)}} \ostate{01}}\\
-    OT'_3 & = \openrule
-             {
-               0 \xrightarrow{l}_{C_5} 0,\\0 \xrightarrow{r}_{C_6} 0,
-               \\ \{\xrightarrow{b2}_Q\},\\b2\neq\delta(y)
-               }
-    {\ostate{01} \xrightarrow{b2} \ostate{01}}\\
-    OT'_4 & = \openrule
-             {
-                       0 \xrightarrow{\delta}_{C_5} 1, ~~
-                       1 \xrightarrow{r}_{C_6} 1, ~~\{\xrightarrow{\delta(y2)}_Q, ~~
-                    \xrightarrow{accept(y2)}_R\} 
-                                 }
-             {\ostate{01} \xrightarrow{\underline{\delta(y2)}} \ostate{11}}    \\
-    OT'_5 & = \openrule
-             {1 \xrightarrow{r}_{C_5} 1,\\\{\xrightarrow{b3}_R\}
-             	}
-             {\ostate{11} \xrightarrow{b3} \ostate{11}}
-    \end{eqnarray*}
-  \end{minipage}
-%  \label{schema:enable5}
-\end{figure}
-
-In this example, we have no state variables in the pNets leaves, so we
-need no auxiliary predicate in the FH-bisimulation.
-
-Let us build a relation
-    $R = \{(A1_0,A2_0), (A1_1,A2_1), (A1_2,A2_2)\}$, and prove that
-    $R$ is a strong FH-bisimulation.
-
-    Pick e.g. transition $OT_1$ of automaton $A1$, we have
-    $A1_0 \xrightarrow{OT_1}_{A1} A1_0$. The matching transition from
-    $A2_0$ is $OT'_1$, with 
-    $A2_0 \xrightarrow{OT'_1}_{A2} A2_0$, the set of holes involved in
-    both transitions is $\{P\}$, and the resulting state is in the
-    bisimulation ($A1_0 ~ A2_0$).
-    The proof obligation is:
-
-    $$  a1\neq\delta(x) \implies
-         a1=b1 \implies b1\neq\delta(y) \land a1=b1 $$
-
-    The proof obligation for $OT_2$ versus $OT'_2$ is still simpler:
-
-    $$ \delta(x_1)=\delta(y_1) \land acc(x_1)=acc(y_1)
-       \implies \underline{\delta(x_1)}=\underline{\delta(y_1)} $$
-
-       the 3 other cases, and the 5 in the other direction, are left
-       to the reader. All are simple to prove, so $R$ is a
-       FH-bisimulation, and the initial states of the 2 pNets are equivalent.
-           \qed
-
-       This proof shows how the flattening induced by the open transitions makes the 
-       reasoning on hierarchical structures easy, while keeping a structured view of the 
-       compared systems.
-
-       \newpage
-
-       \section{Proofs of basic properties on pNets}
-       \subsection{Equivalence relation (Theorem~\ref{thm-equiv})}
-        \emph{Suppose $\mathcal{R}$ 
-       	is an FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, 
-       	$\mathcal{R}$ is 
-       	reflexive, symmetric and transitive.
-       	}
-       \begin{proof}
-
-       It is trivial to check reflexivity and symmetry. Here we focus on the
-transitivity. 
-To prove transitivity of strong FH-bisimulation on pNets it is sufficient to prove 
-transitivity of the strong FH-bisimulation on states. Consider 3 open automata 
-$\mathcal{T}_1$, $\mathcal{T}_2$, $\mathcal{T}_3$ and states $s^1$, $s^2$, $s^3$ in those 
-automata\footnote{We omit the constraints stating that each $s^i_x$ is in the states of 
-$\mathcal{T}_i$ for the sake of readability}.
-Suppose we have $\mathcal{R}$ an FH-bisimulation relation between states of 
-$\mathcal{T}_1$ and of  $\mathcal{T}_2$; members of $\mathcal{R}$ are of the form 
-$(s^1,s^2|\Pred)$.
-Suppose we also  have $\mathcal{R}'$ an FH-bisimulation relation between states of 
-$\mathcal{T}_2$ and of  $\mathcal{T}_3$; members of $\mathcal{R}2$ are of the form 
-$(s^2,s^3|\Pred\,')$.
-
-Let $\mathcal{R}''$ be the relation: 
-\[\mathcal{R}'' = \{(s^1,s^3|\Pred\,'')|\,\Pred\,''=\bigvee_{ \begin{array}{l}
-(s^1,s^2|\Pred)\in\mathcal{R}\\ (s^2,s^3|\Pred\,')\in\mathcal{R}' 	
-\end{array}
-}\,\Pred\land\Pred\,'\}\]
-
-The relation is built as follows: for each pair of state $s^1$, $s^3$, for each state 
-$s^2$ such that $\mathcal{R}$ relates $s^1$ and $s^2$, and $\mathcal{R}'$ relates $s^2$ 
-and $s^3$, we take the conjunction of the two predicates. The predicates for different 
-values of $s^2$ are collected by a disjunction.
- we will show
-that $\mathcal{R}''$ is an FH-bisimulation. Let
-$(s^1,s^2|\Pred)\in\mathcal{R}$,  we have the followings since
-
-\TODO{LUDO: I stopped rewriting here}
-For any open transition $OT$ in $\mathcal{T}_1$:
-
-\begin{mathpar}
-
-\inferrule*[myfraction=\reddottedrule]
-{\{s^1_i\xrightarrow{a_i}_i s^{1'}_i\}^{i\in I_1}, % , s^1_i,s^{1'}_i\in
-	%States(I_1)
-	\{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
-{s^1 \xrightarrow {v} s^{1'}}
-
-\end{mathpar}
-
-there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
-
-\begin{mathpar}
-
-%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
-\inferrule*[myfraction=\reddottedrule]
-{\{s^{2}_i\xrightarrow{a_{i x}}_i s^{2}_{i x}\}^{i\in I_{2 x}},
-	\{\xrightarrow{b_{j x}}_j\}^{j\in J_{2x}}, \Pred_{OT_x},\Post_{OT_x}}
-{s^2 \xrightarrow {v_x} s^{2}_x}
-%         \right)
-\end{mathpar}
-
-such that  $\forall x, J_1=J_{2x}, (s^{1'},s^{2}_x|\Pred_{target_x})\in 
-\mathcal{R}$;
-and  \\
-
-$\Pred \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-\left( \forall j. b_j=b_{jx}  \Rightarrow \Pred_{OT_x}
-\land v\!=\!v_x \land
-\Pred_{target_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
-
-for any open transition $OT_x$, since
-$(s^2,s^3|\Pred^\prime)\in\mathcal{R}$ there exist open transitions
-$OT_{xy}^{x\in X, y\in Y} \subseteq \mathcal{T}_3$:
-
-\begin{mathpar}
-
-%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
-\inferrule*[myfraction=\reddottedrule]
-{\{s^{3}_i\xrightarrow{a_{i x y}}_i s^{3}_{i xy}\}^{i\in I_{3 xy}},
-	\{\xrightarrow{b_{j x y}}_j\}^{j\in J_{3xy}}, \Pred_{OT_{xy}},\Post_{OT_{xy}}}
-{s^3 \xrightarrow {v_{xy}} s^{3}_{xy}}
-%         \right)
-
-\end{mathpar}
-\TODO{LUDO: I have trouble doing computing the next line without intermediates: it is an 
-iterative application of many FH bisim definitions with reordering of terms and 
-manipulation of quantifiers}
-such that  $\forall x, \forall y, J_1=J_{2x}=J_{3xy}, 
-(s^{1'},s^{3}_{xy}|\Pred_{target_{xy}})\in \mathcal{R}$; and  \\
-$\Pred\,' \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}
-\left( \forall j. b_j=b_{jx}=b_{jxy}  \Rightarrow \Pred_{OT_{xy}}
-\land v\!=\!v_{xy} \land
-\Pred_{target_{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{xy}}}\right)$.
-
-\TODO{the proof is incomplete because it does not deal with predicates and does not 
-explicit what is the right $pred''$ $\implies$ TODO}
-
-       \end{proof}
-
-       \bigskip
-
-       The proof of the other theorems rely on two main lemmas,
-dealing respectively with the decomposition of a composed behaviour
-between the context and the internal pNet, and with their recomposition. 
-We start with decomposition: from one open transition of $P[Q]_{j_0}$, we exhibit 
-corresponding behaviours of $P$ and $Q$, and determine the relation between their 
-predicates:
-
-\begin{lemma}[OT decomposition]\label{lem-decompose} 
-	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose:
-	\[ P[Q]_{j_0}   % = \mylangle \pNet_i^{i\in I}, S_j^{j\in J}, 
-	%\symb{SV}_k^{k\inK}\myrangle
-		\models
-		{\inferrule*[myfraction=\reddottedrule]
-			{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I},
-				\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred,  
-				\Post}
-			{\ostate{s_i^{i\in L}} \xrightarrow {v}
-				\ostate{s_i^{\prime i\in L}}}
-		}
-	\]
-		with $Q$ ``moving'' (i.e. $J\cap\Holes(Q)\neq\emptyset$ or $I\cap L_Q\neq 
-		\emptyset$).
-		 Then there exist $v_Q$, $\Pred'$, $\Pred''$, 
-		$\Post'$, $\Post''$ s.t.:\\[-2ex]
-		%\[
-		\begin{mathpar}
-		P\models{\inferrule*[myfraction=\reddottedrule]
-			{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I\setminus L_Q},
-				\{\xrightarrow{b_j}_j\}^{j\in J\setminus \Holes(Q) \cup \{j_0\}}, 
-				\Pred',  
-				\Post'}
-			{\ostate{s_i^{i\in L\setminus L_Q}} \xrightarrow {v}
-				\ostate{s_i'^{\, i\in L\setminus L_Q}}}
-		}%\]
-	\vspace{-2.2ex}\\\text{and~~}
-		%\[
-		Q\models{\inferrule*[myfraction=\reddottedrule]
-			{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I\cap L_Q},
-				\{\xrightarrow{b_j}_j\}^{j\in J\cap\Holes(Q)}, \Pred'',  
-				\Post''}
-			{\ostate{s_i^{i\in L_Q}} \xrightarrow {v_Q}
-				\ostate{s_i'^{\, i\in L_Q}}}
-		}%\]
-		\end{mathpar}
-		and  $\Pred\subst{v_Q\leftarrow b_{j_0}} =(\Pred'
-		\land \Pred'')$, $\Post=\Post'\uplus 
-		\Post''$ where $\Post''$ is the restriction of $\Post$ over variables of 
-		$\Leaves(Q)$.
-\end{lemma}
-
-   \begin{small}\begin{proof}
-       Consider each premise of the open transition (as constructed by rule TR2 in Definition~\ref{def:operationalSemantics}). 
-We know each premise is true for $P[Q]_{j_0}$ and try to prove the equivalent premise for 
-$P$. 
-First, $K$ and the synchronisation vector $SV_k$ are unchanged\footnotemark (however 
-$j_0$ passes from 
-the set of subnets to the set of holes). Then $SV=clone(\alpha_j^{j\in I_k\uplus\{j_0\}\uplus 
-J_k})$. $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$. 
-Now focus on OTs of the subnets\footnotemark[\thefootnote]:\\[-2ex]
-\[\forall m\in I_k\cup \{j_0\}.
-\pNet_m \models
-\inferrule*[myfraction=\reddottedrule]
-{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m},
-	\{\xrightarrow{b_{j}}_j\}^{j\in J_m}, \Pred_m, \Post_m}
-{\ostate{s_{i}^{i \in L_m}} \xrightarrow {v_m}
-	\ostate{s_{i}^{\prime\ i \in L_m}}}\]
-Only elements of $I_k$ are useful to assert the premise for reduction of $P$; the last 
-one ensures (note that $Q$ is at place $j_0$, and by definition of the open transition 
-for $P[Q]_{j_0}$, $I_{j_0}=I\cap L_Q$, 
-$L_{j_0}=L_Q$):\\[-2ex]
-	\[Q\models{\inferrule*[myfraction=\reddottedrule]
-		{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I\cap L_Q},
-			\{\xrightarrow{b_j}_j\}^{j\in J\cap\Holes(Q)}, \Pred_{j_0},  
-			\Post''}
-		{\ostate{s_i^{i\in L_Q}} \xrightarrow {v_{j_0}}
-			\ostate{s_i'^{\, i\in L_Q}}}
-	}\]
-This already ensures the second part of the conclusion if we 
-choose\footnotemark[\thefootnote]  $v_Q=v_{j_0}$ ($\Pred''= \Pred_{j_0}$). Now let $I'= 
-\biguplus I'_m=I\setminus L_Q$, $J'=\biguplus J'_m\uplus J_k 
-\uplus\{j_0\}=J\setminus\Holes(Q)\uplus \{j_0\}$; the predicate is 
-$\Pred'=\bigwedge_{m\in I_k}\Pred_m 
-\land \Pred(SV,a_i^{i\in I_k},b_j^{j\in J_k\cup \{j_0\}},v)$
-where\footnotemark[\thefootnote] $\Pred(SV,a_i^{i\in I_k},b_j^{j\in 
-J_k},v)\Leftrightarrow 
-\forall i\in I_k.\, \alpha_i=a_i\land \forall j \in J_k\cup \{j_0\}.\, \alpha_j=b_j \land 
-v=\alpha'_k 
-$. Modulo renaming of fresh variables, this is identical to the predicate that occurs in 
-the source open transition except $\alpha_{j_0}=v_{j_0}$ has been replaced by  
-$\alpha_{j_0}=b_{j_0}$.
-Thus, $\Pred\subst{v_Q\leftarrow b_{j_0}}=(\Pred' 
-\land \Pred'')$. %\TODO{the argument on renaming has mostly been
-                 %removed is it still OK? yes.}. 
-Finally, Post 
-%conditions are easily split\footnote{\TODO{moved. could
-%    even remove...?}Note that if the rules are not simplified, no
-%  post-condition range over the variables of $P$ and $Q$ at the same
-%  time} 
-into conditions of the context $P$ and the pNet $Q$ (they are
-builts similarly as they only deal with  
-leaves): $\Post=\Post'\uplus \Post''$. This concludes the 
-proof as we checked all the premises of the open transition for both $P$ and $Q$.\qed
-\footnotetext{Cloning and freshness introduce alpha-conversion at many points 
-of the proof; we 
-	only 
-	give major arguments concerning alpha-conversion to make the proof readable; in 
-	general, fresh variables appear in each transition inside
-        terms $b_j$, $v$, and 
-	$\Pred$.}
-\end{proof}
-   \end{small}
-
-In general, the actions that can be emitted by $Q$ is  a subset of the possible 
-actions of the holes, and the predicate involving $v_Q$ and the synchronisation vector is 
- more restrictive than the one involving only the variable $b_{j_0}$. This has no impact 
- on the previous proof and this restriction  results from the composition of predicates.
-%\TODO{is this useful? = yes, I think }
-
-Lemma \ref{lem-compose} is combining an open transition of $P$ with
-an open transition of $Q$, and building a corresponding transition of
-$P[Q]_{j_0}$, assembling their predicates.
-
-\begin{lemma}[Open transition composition]\label{lem-compose} 
-	Suppose $j_0\in J$ and:\\[-2ex]
-\begin{mathpar}
-%\[
-P\models{\inferrule*[myfraction=\reddottedrule]
-	{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I},
-		\{\xrightarrow{b_j}_j\}^{j\in J}, \\\\
-		\Pred,  
-		\Post}
-	{\ostate{s_i^{i\in L}} \xrightarrow {v}
-		\ostate{s_i'^{\, i\in L}}}
-}%\]
-\text{~and~}
-%\[
-Q\models{\inferrule*[myfraction=\reddottedrule]
-	{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I_Q},
-		\{\xrightarrow{b_j}_j\}^{j\in J_Q},\\\\
-		 \Pred',  
-		\Post'}
-	{\ostate{s_i^{i\in L_Q}} \xrightarrow {v_Q}
-		\ostate{s_i'^{\, i\in L_Q}}}
-}%\]
-\end{mathpar}
-Then, we have\\[-2ex]
-	\[ P[Q]_{j_0}   % = \mylangle \pNet_i^{i\in I}, S_j^{j\in J}, 
-	%\symb{SV}_k^{k\inK}\myrangle
-	\models
-	{\inferrule*[myfraction=\reddottedrule]
-		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I \uplus I_Q},
-			\{\xrightarrow{b_j}_j\}^{j\in J\setminus\{j_0\} \uplus J_Q}, 
-			\Pred\subst{b_{j_0}\leftarrow v_Q}\land\Pred',  
-			\Post\uplus \Post'}
-		{\ostate{s_i^{i\in L\uplus L_Q}} \xrightarrow {v}
-			\ostate{s_i^{\prime i\in L\uplus L_Q}}}
-	}
-	\]
-\end{lemma}
-\begin{small}
-
-\begin{proof}
-
-       Consider each premise of the open transition (constructed by TR2 in 
-Definition~\ref{def:operationalSemantics}). 
-We know each premise is true for $P$ and try to prove the equivalent premise for 
-$P[Q]_{j_0}$ (using the open transition of $Q$). 
-$K$ and the synchronisation vector are unchanged ($j_0$ is now in the set of sub-pNets); 
-$SV=clone(\alpha_j^{j\in I_k\uplus\{j_0\}\uplus 
-	J_k})$. $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$. All subpNets can be 
-reduced:\\[-2ex]%\footnote{again we skip arguments related to renaming of fresh 
-%variables}:
-\[\forall m\in I_k\cup \{j_0\}.
-\pNet_m \models
-\inferrule*[myfraction=\reddottedrule]
-{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I'_m},
-	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
-{\ostate{s_{i}^{i \in L_k}} \xrightarrow {v_m}
-	\ostate{s_{i}^{\prime\ i \in L_k}}}\]
-the last sub-pNet is the one filled by $Q$ which offers an open transition by hypothesis.
-Let $I'=\biguplus_{m\in I_k} I_m \uplus I_Q = I \uplus I_Q$ and $J'= \biguplus_{m\in I_k} 
-J_m \uplus J_Q \uplus J_k = J\setminus\{j_0\}\uplus J_Q$. The predicate for the open 
-transition is: $\Pred''=\bigwedge_{m\in I_k}\Pred_m \land \Pred'
-\land \Pred(SV,a_i^{i\in I_k}\uplus(j_0\mapsto v_Q),b_j^{j\in J_k},v)$. By definition 
-$\Pred(SV,a_i^{i\in I_k}\uplus(j_0\mapsto v_Q),b_j^{j\in J_k},v)\Leftrightarrow
-	\forall i\in I_k.\, a_i=\alpha_i\land \forall j \in J_k.\, b_j=\alpha_j \land 
-	\alpha'_k=v\land v_Q=\alpha_{j_0}$, finally $\Pred''=\Pred\subst{b_{j_0}\leftarrow 
-	v_Q} \land \Pred'$. The post-condition gathers the post-conditions related to all 
-	the leaves. Finally, the composed open transition can be
-        built. \qed
-        \end{proof}
-\end{small}
-
-         \newpage
- \section{Proof of Theorem ~\ref{thm-congr-eq}}
- The proof of Theorem~\ref{thm-congr-eq} exhibits classically a bisimulation relation for 
- a 
- composed system.  It considers then an open transition of $P[Q]_{j_0}$ that should be 
- simulated. It then uses  Lemma~\ref{lem-decompose} to decompose the open transition 
- of $P[Q]_{j_0}$ and obtain an open transition of $P$ and $Q$; the FH-bisimulation 
- property can 
- be applied  to $Q$ to obtain an equivalent family of open transitions of $Q'$; this 
- family is 
- then recomposed by Lemma~\ref{lem-compose} to build a set of open transitions of 
- $P[Q']_{j_0}$ 
- that will simulate the original one.
-
- Let $\Leaves(Q)=p_l^{l\in L}$, $\Leaves(Q')={p'}_l^{l\in L'}$, 
- $\Leaves(P)=p_l^{l\in L_P}$.
- Consider $Q$ FH-bisimilar to $Q'$. It means that there is a relation 
- $\mathcal{R}$ that is an FH-bisimulation between the open automata of the two pNets. 
- We will consider the relation $\mathcal{R}'=\{(s_1,s_2|\Pred)|s_1=s'_1\uplus s \land 
- s_2=s'_2\uplus s \land s\in \mathcal{S}_P \land (s_1',s_2'|\Pred)\in\mathcal{R}\}$ 
- where $\mathcal{S}_S$ is the set of states of the open automaton of $P$.	We will prove 
- that $\mathcal{R}'$ is an open FH-bisimulation. Consider a pair of FH-bisimilar 
- states: $(\ostate{s_{1 i}^{i \in L_P\uplus L}},\ostate{{s}_{2 i}^{i \in L'}\uplus 
- 	{s}_{1 i}^{i \in L_P}}|\Pred)\in\mathcal{R}'$. %Those are states of the open 
- %	automata of 
- %	the pNets $P[Q]_{j_0}$ and $P'[Q]_{j_0}$. 
- Consider an 
- open transition $OT$ of $P[Q]_{j_0}$. %We need to find a family ${OT}_x^{x\in X}$ of 
- %	open transitions of $P'[Q]_{j_0}$ that satisfy the conditions of
- %	Definition~\ref{def-FH-bisim}. $OT$ is of the form 
- \\[-2ex]     
- \[P[Q]_{j_0}\models\inferrule*[myfraction=\reddottedrule]
- {\{s_i\xrightarrow{a_i}_i s'_i\}^{i\in I}, % , s^1_i,s^{1'}_i\in 
- 	%States(I_1)
- 	\{\xrightarrow{b_j}_j\}^{j\in J},\Pred_{OT},\Post_{OT}}
- { \ostate{s_{1 i}^{i \in L_P\uplus L}}\xrightarrow {v} \ostate{{s'}_{1 i}^{i \in 
- 			L_P\uplus 
- 			L}}}\]
- Let $J'=J\setminus \Holes(Q) \cup \{j_0\}$.	 By 
- Lemma~\ref{lem-decompose} we have :\\[-2ex]
- 	\begin{mathpar}
- P\models{\inferrule*[myfraction=\reddottedrule]
- 	{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I\setminus L},
- 		\{\xrightarrow{b_j}_j\}^{j\in J'}, 
- 		\Pred\,',  
- 		\Post'}
- 	{\ostate{s_{1 i}^{i\in L_P}} \xrightarrow {v}
- 		\ostate{s_{1 i}'^{\, i\in L_P}}}
- }\\
- Q\models{\inferrule*[myfraction=\reddottedrule]
- 	{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I\cap L},
- 		\{\xrightarrow{b_j}_j\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
- 		\Post''}
- 	{\ostate{s_{1 i}^{i\in L}} \xrightarrow {v_Q}
- 		\ostate{s_{1 i}'^{\, i\in L}}}
- }\end{mathpar}
- and  $\Pred_{OT}\subst{v_Q\leftarrow b_{j_0}} =({\Pred\,}'
- \land {\Pred\,}'')$, $\Post_{OT}=\Post'\uplus 
- \Post''$ ($\Post''$ is the restriction of $\Post$ over variables of 
- $\Leaves(Q)$). As $Q$ is FH-bisimilar to $Q'$ and $(\ostate{s_{1 i}^{i \in 
- 		L}},\ostate{{s}_{2 i}^{i \in L'}}|\Pred)\in\mathcal{R}$ there is a family 
- $OT'_x$ 
- of 	open transitions of the automaton of $Q'$ such that\\[-2ex] 
- \begin{mathpar}
- Q'\models\inferrule*[myfraction=\reddottedrule]
- {\{s_{2 i}\xrightarrow{a_{i x}}_i s_{2 i x}\}^{i\in I_{x}},
- 	\{\xrightarrow{b_{j x}}_j\}^{j\in J\cap\Holes(Q)}, 
- 	\Pred_{OT_x},\Post_{OT_x}}
- {\ostate{s_{2 i}^{i\in L'}} \xrightarrow {v_x} \ostate{s_{2 i x}^{i\in L'}}}
- \end{mathpar}
- and  $\forall x, (\ostate{s_{1 i}^{i\in L}},\ostate{s_{2 i x}^{i\in 
- 		L'}}|\Pred_{tgt_x})\in 
- \mathcal{R}$; 
- and  \\
- $\Pred \land \Pred\,''
- \Rightarrow \bigvee_{x\in X}
- \left( \forall j\in J\cap \Holes(Q). b_j=b_{jx}  \Rightarrow 
- \Pred_{OT_x}
- \land v_Q\!=\!v_x \land  
- \Pred_{tgt_x}\subst{\Post''}\subst{\Post_{OT_x}}\right)$
-
- We can now apply Lemma~\ref{lem-compose} on each of the $OT'_x$ together with 
- the transition of $P$ and obtain a new family $OT_x$ of open transitions (where for 
- $i\in L_P$, $s_{2 i}=s_{1 i}$ and $s_{2 i x}=s'_{1 i}$, and for $j\in Holes(P)$, 
- $b_{j x}=b_j$):\\[-2ex]
- \[ P[Q']_{j_0}  
- \models
- {\inferrule*[myfraction=\reddottedrule]
- 	{\{s_{2 i}\xrightarrow{a_{i x}}_i {s}_{2 i x}\}^{i\in I_x \uplus 
- 			(I\cap L_P)},
- 		\{\xrightarrow{b_{j x}}_j\}^{j\in J}, \\
- 		\Pred\,'\subst{b_{j_0 x}\leftarrow v_x}\land\Pred_{OT_x},  
- 		\Post'\uplus \Post_{OT_x} }
- 	{\ostate{s_{2 i }^{i\in L'\uplus L_Q}} \xrightarrow {v_x}
- 		\ostate{{s}_{2 i x}^{i\in L'\uplus L_Q}}}
- }
- \]
-
- Observe that we used the fact that $J=(J\setminus\Holes(Q)\cup 
- \{j_0\})\setminus\{j_0\}\cup 
- (J\cap\Holes(Q))$. Now we have to verify the conditions for the 
- FH-bisimulation between $OT$ and $OT_x$.
- $\forall x, (\ostate{{s'}_{1 i}^{i\in L_P\uplus L}},\ostate{s_{2 i 
- 		x}^{i\in L_P\uplus L'}}|\Pred_{tgt_x})\in 
- \mathcal{R}'$ (by definition of
- $\mathcal{R}'$) and in four steps we get:
-
- \noindent                        
- \begin{small} $\Pred \land \Pred_{OT} \implies
- 	\Pred\land(\Pred\,'\land \Pred\,'')\subst{b_{j_0}\leftarrow v_Q}\\ % reversed 
- 	%substitution 
- 	\implies 
- 	(\Pred\land\Pred\,'')\land \Pred\,'\subst{b_{j_0}\leftarrow v_Q}\\ % $b_{j_0}$ only 
- 	%appears 
- 	%in $\Pred\,'$
- 	\implies  \hspace{-2ex}
- 	{\displaystyle\bigvee_{x\in X}
- 	\left( \forall j\in J\cap \Holes(Q). b_j=b_{jx}  \Rightarrow 
- 	\Pred_{OT_x}
- 	\land v_Q\!=\!v_x \land  
- 	\Pred_{tgt_x}\subst{\Post''}\subst{\Post_{OT_x}}\right)
- }
- \\~\qquad\qquad	\land \Pred\,'\subst{b_{j_0}\leftarrow v_Q} \\
- 	\implies
- 	 \hspace{-2ex}
- 	{\displaystyle\bigvee_{x\in X}
- 		\left( \forall j\in J\cap \Holes(Q). b_j=b_{jx}  \Rightarrow 
- 		\Pred\,'\subst{b_{j_0}\leftarrow v_x}\land \Pred_{OT_x}
- 		\land v_Q\!=\!v_x \land  
- 		\Pred_{tgt_x}\subst{\Post''}\subst{\Post_{OT_x}}\right)
- 	}
- 	$\end{small}
-
- %\TODO{There was a confusion between the $\Rightarrow$ between the
- %  steps, and the $\implies$ inside the formulas...}
-
- Explanations: first, we reversed the substitution; then we
- restricted the 
- substitution as $b_{j_0}$ only appears in $\Pred\,'$; then we
- applied the property of FH-bisimulation for $P$ and rearranged the
- terms using the fact that $v_Q=v_x$. The obtained formula reaches the goal except for 
- two points:\\[-4.3ex] 
- \begin{itemize}
- 	\item We need $\forall j\!\in\! J$ instead of $\forall j\!\in\! J\cap\Holes(Q)$  but  
- 	adding prerequisite on more variables 
- 	does not 
- 	change the validity of the formula (those variables are not used).
- 	\item Concerning the last term, we need 
- 	$\Pred_{tgt_x}\subst{\Post_{OT}}\subst{\Post'\uplus \Post_{OT_x}}$ 
- 	, i.e.:
- 	$\Pred_{tgt_x}\subst{\Post'\uplus 
- 		\Post''}\subst{\Post'\uplus \Post_{OT_x}}$. We 
- 	can conclude by observing that	$\Pred_{tgt_x}$ does not use any variable of $P$ 
- 	and thus $\subst{Post'}$ has no effect.
- \end{itemize}	
- This proves the  condition of the FH-simulation, the other direction is 
- similar.\qed
-
-        \newpage
-        \section{Proof of Theorem ~\ref{thm-ctxt-eq}}
-The proof of Theorem~\ref{thm-ctxt-eq} exhibits  a bisimulation relation for a 
-composed system. It then uses  Lemma~\ref{lem-decompose} to decompose the open transition 
-of $P[Q]_{j_0}$ and obtain an open transition of $P$ on which the FH-bisimulation 
-property can 
-be applied  to obtain an equivalent family of open transitions of $P'$; this family is 
-then recomposed by Lemma~\ref{lem-compose} to build a set of open transitions of 
-$P'[Q]_{j_0}$ 
-that will simulate the original one.
-
-        Let $\Leaves(Q)=p_l^{l\in L_Q}$, 
-$\Leaves(P)=p_l^{l\in L}$, $\Leaves(P')={p'}_l^{l\in L'}$.
-	Consider $P$ FH-bisimilar to $P'$. It means that there is a relation 
-	$\mathcal{R}$ that is an FH-bisimulation between the open automata of the two pNets. 
-	We will consider the relation $\mathcal{R}'=\{(s_1,s_2|\Pred)|s_1=s'_1\uplus s \land 
-	s_2=s'_2\uplus s \land s\in \mathcal{S}_Q \land (s_1',s_2'|\Pred)\in\mathcal{R}\}$ 
-	where $\mathcal{S}_Q$ is the set of states of the open automaton of $Q$.	We will prove 
-	that $\mathcal{R}'$ is an open FH-bisimulation. Consider a pair of FH-bisimilar 
-	states: $(\ostate{s_{1 i}^{i \in L\uplus L_Q}},\ostate{{s}_{2 i}^{i \in L'}\uplus 
-	{s}_{1 i}^{i \in L_Q}}|\Pred)\in\mathcal{R}'$. %Those are states of the open 
-%	automata of 
-%	the pNets $P[Q]_{j_0}$ and $P'[Q]_{j_0}$. 
-Consider an 
-	open transition $OT$ of $P[Q]_{j_0}$. %We need to find a family ${OT}_x^{x\in X}$ of 
-%	open transitions of $P'[Q]_{j_0}$ that satisfy the conditions of
-%	Definition~\ref{def-FH-bisim}. $OT$ is of the form 
-\\[-2ex]     
-	\[P[Q]_{j_0}\models\inferrule*[myfraction=\reddottedrule]
-	{\{s_i\xrightarrow{a_i}_i s'_i\}^{i\in I}, % , s^1_i,s^{1'}_i\in 
-		%States(I_1)
-		\{\xrightarrow{b_j}_j\}^{j\in J},\Pred_{OT},\Post_{OT}}
-	{ \ostate{s_{1 i}^{i \in L\uplus L_Q}}\xrightarrow {v} \ostate{{s'}_{1 i}^{i \in 
-	L\uplus 
-	L_Q}}}\]
-Let $J'=J\setminus \Holes(Q) \cup \{j_0\}$.	 By 
-	Lemma~\ref{lem-decompose} we have :\\[-2ex]
-			\begin{mathpar}
-				P\models{\inferrule*[myfraction=\reddottedrule]
-				{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I\setminus L_Q},
-					\{\xrightarrow{b_j}_j\}^{j\in J'}, 
-					\Pred\,',  
-					\Post'}
-				{\ostate{s_{1 i}^{i\in L}} \xrightarrow {v}
-					\ostate{s_{1 i}'^{\, i\in L}}}
-			}\\
-			Q\models{\inferrule*[myfraction=\reddottedrule]
-				{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I\cap L_Q},
-					\{\xrightarrow{b_j}_j\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
-					\Post''}
-				{\ostate{s_{1 i}^{i\in L_Q}} \xrightarrow {v_Q}
-					\ostate{s_{1 i}'^{\, i\in L_Q}}}
-			}\end{mathpar}
-			and  $\Pred_{OT}\subst{v_Q\leftarrow b_{j_0}} =({\Pred\,}'
-			\land {\Pred\,}'')$, $\Post_{OT}=\Post'\uplus 
-			\Post''$ ($\Post''$ is the restriction of $\Post$ over variables of 
-			$\Leaves(Q)$). As $P$ is FH-bisimilar to $P'$ and $(\ostate{s_{1 i}^{i \in 
-			L}},\ostate{{s}_{2 i}^{i \in L'}}|\Pred)\in\mathcal{R}$ there is a family 
-			$OT'_x$ 
-			of 	open transitions of the automaton of $P'$ such that\\[-2ex] 
-			\begin{mathpar}
-			%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
-			P'\models\inferrule*[myfraction=\reddottedrule]
-			{\{s_{2 i}\xrightarrow{a_{i x}}_i s_{2 i x}\}^{i\in I_{x}},
-				\{\xrightarrow{b_{j x}}_j\}^{j\in J'}, 
-				\Pred_{OT_x},\Post_{OT_x}}
-			{\ostate{s_{2 i}^{i\in L'}} \xrightarrow {v_x} \ostate{s_{2 i x}^{i\in L'}}}
-			%         \right)
-			\end{mathpar}
-			and  $\forall x, (\ostate{s_{1 i}^{i\in L}},\ostate{s_{2 i x}^{i\in 
-			L'}}|\Pred_{tgt_x})\in 
-			\mathcal{R}$; 
-			and  \\
-			$\Pred \land \Pred'
-		 \Rightarrow \bigvee_{x\in X}
-			\left( \forall j\in J'. b_j=b_{jx}  \Rightarrow 
-			\Pred_{OT_x}
-			\land v\!=\!v_x \land  
-			\Pred_{tgt_x}\subst{\Post'}\subst{\Post_{OT_x}}\right)$
-			%     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x}) \right)$.
-
-			We can now apply Lemma~\ref{lem-compose} on each of the $OT'_x$ together with 
-			the transition of $Q$ and obtain a new family $OT_x$ of open transitions (where for 
-			$i\in L_Q$, $s_{2 i}=s_{1 i}$ and $s_{2 i x}=s'_{1 i}$, and for $j\in Holes(Q)$, 
-			$b_{j x}=b_j$):\\[-2ex]
-				\[ P'[Q]_{j_0}   % = \mylangle \pNet_i^{i\in I}, S_j^{j\in J}, 
-				%\symb{SV}_k^{k\inK}\myrangle
-				\models
-				{\inferrule*[myfraction=\reddottedrule]
-					{\{s_{2 i}\xrightarrow{a_{i x}}_i {s}_{2 i x}\}^{i\in I_x \uplus 
-					(I\cap L_Q)},
-						\{\xrightarrow{b_{j x}}_j\}^{j\in J}, \\
-						\Pred_{OT_x}\subst{b_{j_0 x}\leftarrow v_Q}\land\Pred\,'',  
-						\Post_{OT_x}\uplus \Post''}
-					{\ostate{s_{2 i }^{i\in L'\uplus L_Q}} \xrightarrow {v_x}
-						\ostate{{s}_{2 i x}^{i\in L'\uplus L_Q}}}
-				}
-				\]
-			Observe that $J=(J\setminus\Holes(Q)\cup \{j_0\})\setminus\{j_0\}\cup 
-			(J\cap\Holes(Q))$. Now we have to verify the conditions for the 
-			FH-bisimulation between $OT$ and $OT_x$.
-			 $\forall x, (\ostate{{s'}_{1 i}^{i\in L\uplus L_Q}},\ostate{s_{2 i 
-			x}^{i\in L'\uplus L_Q}}|\Pred_{tgt_x})\in 
-			\mathcal{R}'$ (by definition of
-                        $\mathcal{R}'$) and in four steps we get:
-
-\noindent                        
-\begin{small} $\Pred \land \Pred_{OT} \implies
- \Pred\land(\Pred\,'\land \Pred\,'')\subst{b_{j_0}\leftarrow v_Q}\\ % reversed 
- %substitution 
- \implies 
- (\Pred\land\Pred')\subst{b_{j_0}\leftarrow v_Q}\land \Pred\,''\\ % $b_{j_0}$ only 
- %appears 
- %in $\Pred\,'$
- \implies  \hspace{-2ex}
-{\displaystyle{\bigvee_{x\in X}\!(\forall j\!\in\! J'. b_j\!=\!b_{jx}  
-\Rightarrow \!
-\Pred_{OT_x}\subst{b_{j_0}\!\!\leftarrow\!\! v_Q}
-\land v\!=\!v_x}} %\\ \hspace*{40mm} %
-\land \Pred_{tgt_x}\subst{\Post'}\subst{\Post_{OT_x}}) \land
-\Pred''\\ % 
-			%FH for P
- \implies  \hspace{-2ex}
- {\displaystyle{\bigvee_{x\in X}\!( \forall j\!\in\! J'. b_j\!=\!b_{jx} \Rightarrow 
-\Pred_{OT_x}\subst{b_{j_0}\!\!\leftarrow\!\! v_Q}\!\land\! \Pred\,''%\\ \hspace*{40mm}
-\!\land\! v\!=\!v_x \!\land\!  
-\Pred_{tgt_x}\subst{\Post'}\subst{\Post_{OT_x}})}} 			
-$\end{small}
-
-%\TODO{There was a confusion between the $\Rightarrow$ between the
-%  steps, and the $\implies$ inside the formulas...}
-
-Explanations: first, we reversed the substitution; then we
-restricted the 
-substitution as $b_{j_0}$ only appears in $\Pred\,'$; then we
-applied the property of FH-bisimulation for $P$ and rearranged the
-terms. The obtained formula reaches the goal except for two points:\\[-4.3ex] 
-\begin{itemize}
-	\item We need $\forall j\!\in\! J$ instead of $\forall j\!\in\! J'$ with 
-	$J'\!=\!J\!\setminus\! \Holes(Q) \cup \{j_0\}$ but the formula under the quantifier 
-	does not depend on 
-	$b_{j_0}$ now (thanks to 
-	the substitution). Concerning $\Holes(Q)$, adding prerequisite on more variables 
-	does not 
-	change the validity of the formula (those variables are not used).
-	\item We need $\Pred_{tgt_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}\uplus \Post''}$ 
-	, i.e.:
-	$\Pred_{tgt_x}\subst{Post'\uplus Post''}\subst{\Post_{OT_x}\uplus \Post''}$. We 
-	can conclude by observing that	$\Pred_{tgt_x}$ does not use any variable of $Q$ 
-	and thus $\subst{Post''}$ has no effect.
-\end{itemize}	
-This proves the  condition of the FH-simulation, the other direction is 
-similar.\qed
-
-  \newpage
-
-  \section{Running example: Hierarchical Broadcast}
-
-Hierarchical Broadcast (HB) is a way of implementing broadcasting
-algorithms within a large set of processes, with better performances
-and scalability. There have been many proposals for hierarchical
-broadcast algorithms (cite...), most of them focussing on specific
-architectures or features (in particular fault tolerance), and on
-performance analysis. Very few have given a formal description of the
-algorithm, allowing to reason about their safety properties.
-In this paper, we choose HB as a running example because it is a
-complex interaction pattern on which the topology and the
-parameterised nature plays a crucial role.
-
-We give here the description of one simple HB algorithm, inspired
-from\cite{Taguchi03}. For the formal description, we define a
-pNet template, that can be used as a building node in a hierarchical
-assembly of processes, organised in a tree of sub-groups. Inside each
-sub-group, messages are sent using  local broadcast; associated to
-each sub-group is a ``gateway'' in charge of the
-transmission of messages, up and down, between the subgroups. The
-gateways are described as generic pLTSs, playing the role of
-``controllers'' in the pNet node.
-
-\begin{figure}[t]
-\centerline{  \includegraphics[width=0.9\linewidth]{XFIG/SchemaHB2}}
-  \caption{Principle of a Hierarchical Broadcast structure and protocol}
-  \label{fig:hb-scenario}
-\end{figure}
-
-Figure \ref{fig:hb-scenario} shows an instantiation of a HB
-structure, and a possible scenario:
-\begin{itemize}
-\item
-  The HB tree has 3 sub-groups, each with its gateway process, and 6
-  processes scattered in the sub-groups.
-\item
-  The path in green shows the sequence of message exchanges when Process P21 (within
-  group G2) sends a message to process P111 (within group G11).
-\item
-  As the target is not within the local group to which P21 belongs,
-  the initial message $m(111)$ is sent up to group 2, and
-  arrives in gateway $gw2$.
-\item
-  Now the destination belongs to a group that is a sibling of G2, so
-  it is broadcast to all its siblings (sent as $bm(111)$, and
-  received as $m(111)$). It will be simply discarded by
-  gateways or processes that are not involved (here P3), while $gw1$
-  will recognize as being of interest, and in next step send it down
-  to its group.
-\item
-  Sending down is again a broadcast, to all members of sub-group
-  G1. Process P12 will ignore it, while gateway $gw11$ in turn
-  will recognize and forward the message.
-\item
-  Within group G11, process P111 will finally receives message
-  $m(111)$, that terminates our scenario.
-\end{itemize}
-
-Along this paper, we will use this example to illustrate the use of
-pNets as a structured semantic model, with a stress on the fact that
-we represent here HB as a program schema, with unspecified process
-arguments, using open pNets. We will show how the symbolic operational
-semantics of open pNets computes the dynamics of the HB in term of a
-symbolic representation that we call open-transitions, and how we can
-prove equivalences between open systems.
-
-\begin{example} \emph{First step: define the action algebra, with data domains,
-    operators and predicates.}
-  For our HB structure, we use send and receive messages encoded
-  respectively as $m(arg)$ and $im(?var)$ with
-  $arg$ of type \texttt{Address}. HB has a message-based
-  structure, and by convention action names for action reception will
-  be prefix by the letter "i". We abstract away
-  from the payload of the messages, keeping only target addresses in the HB
-  tree as an argument to all messages. Addresses are finite sequences
-  of natural numbers written \texttt{s.i}
-  with \texttt{s} a sequence and i a number. In concrete instantiations, we
-  assume numbers are simple digits, and we write the sequences without
-  the dot, as in ``121''. Then in the model of the
-  gateways, we must be able to decide whether an address is below/above the
-  current address, or in some specific relation, using
-  predicates:\\
-  - \emph{i==j} Syntactic equality between two sequences.\\
-  - \emph{is\_ancestor(i,j)}: $i$ is a (strict) prefix of $j$.\\
-  - \emph{is\_direct\_relative(i,j)}: $i$ and $j$ have a common prefix $k$, $i=k.i1$, $j=k.j1$, with $i1$ of length 1, but $j1$ can be of length equal or greater than 1 ($j$ is a brother or a nephew in the genealogy).\\
-  - \emph{is\_other\_relative(i,j)}: all other cases.\\
-  Note that these 4 predicates are exclusive.
-\end{example}
-
-\begin{example}  \emph{Second step: define the gateway behaviour as a pLTS.}
-
-\begin{figure}[h]
-\centerline{  \includegraphics[width=0.85\linewidth]{ATG/GatewayHB}}
-\caption{Behaviour of a Gateway controller %\TODO{ERIC: change the action syntax}
-  }
-  \label{fig:hb-HBgateway}
-\end{figure}
-Figure \ref{fig:hb-HBgateway} shows the pLTS representing the generic
-gateway controller. From its initial state, it can receive messages
-$ium(?tgt)$ from the subgroup below, or $im(?tgt)$
-coming either from above or from an horizontal broadcast. The details will
-be explained later, together with the model structure and the
-protocol.
-To simplify the notation in the pLTS drawings, we use the following
-conventions: state variables are implicitely subscripted by the
-adequate state number (e.g. $ium(?tgt)$ means $ium(?tgt_2)$), and we
-have ``global'' variables that are defined in all states (here $gid$
-means $gid_0,gid_1,gid_2$).
-
-Note that we use \texttt{if-then-else} or \texttt{case}
-constructs in the pLTS labels. These are mere abbreviations, that can
-be expanded as a set of transitions carrying simple labels with adequate guards.
-\end{example}
-
-\begin{example} \emph{Sorts of pLTSs:}
-  The sort of the gateway in Figure \ref{fig:hb-HBgateway} is:\\
-  $\large\{ um(tgt_s), im(tgt_s), dm(tgt_s), bm(tgt_s), um(tgt_s),
-  ium(tgt_s), DISCARD, \\ERROR(name) \large\}_{s\in\{1,2\}}$
-\end{example}
-
-\begin{figure}[t]
-  \includegraphics[width=1.0\linewidth]{ATG/Inst5}
-  \caption{A Hierarchical Broadcast pNet Structure}\label{fig:hb-pnet-graphical}
- \end{figure}
-
-\begin{example} \emph{pNet structure, and graphical representation}  
-Here we show some parts of the pNet tree expressing our HB
-structure. Figure \ref{fig:hb-pnet-graphical} shows the full pNet
-model in a graphical format, where each box represents a pNet node
-(Groot, G1, ..., G11), a pLTS (gw1, ..., gw11), or a process (P3, ...,
-P111).
-The actions in the sorts of the nodes appear as ports on the boxes,
-and the synchronisation vectors as arrows, or multipoint ``webs''
-drawn as ellipses. For
-example, the webs
-%labelled \texttt{tau}
-in the Groot box
-  correspond to synchronisation vectors expressing a broadcast
-  communication from one of the subnets of Groot (gw1, gw2, or P3), to
-  the others.
-
-  Formally, the root pNet has a structure $<gw1, gw2, G1, G2, P3>$,
-  with G1 and G2 sub-pNets, their associated gateways gw1, gw2
-  pLTSs, and P3 a process Hole. We have 4 possible broadcast communications at the
-  root, corresponding to as many synchronisation vectors; e.g. if gw2 is the sender:
-  $< im(a), bm(a), -, -, im(a)> \to\!\underline{bm(a)}$.
-
-  We define the synchronisation vectors in a parameterised way
-  (independently of a specific HB network configuration) for any
-  pNet node in a HB structure. Let $\widetilde{i}$ be the position of this pNet in the
-  structure.
-   We define here 4 of these synchronisation vectors, that we will
-   use in the next sections to illustrate the semantic rules.
-   %; the full table is listed in Appendix \ref{Appendix:SynchVectors}.
-   In the
-  vectors below,
-  $\widetilde{I_G}=\{gw\widetilde{i}1,..,gw\widetilde{i}p,G\widetilde{i}1,..,G\widetilde{i}p\}$
-   and
-  $\widetilde{I_P}=\{P\widetilde{i}1,..,P\widetilde{i}p\}$ are the sets
-  containing respectively the indexes of sub-nets and holes of the
-  pNet node, $\widetilde{I_{G+P}}$ their union.
-
-  \begin{figure}[h!]
-  \label{fig:HBvectors}
-  \begin{tabular}{|p{1.4cm}|p{11cm}|}
-%% \hline\hline
-%% \multicolumn{3}{|l|}{Hierarchical broadcasting}\\
-  \hline
-  \hline
-$(UG)_{\widetilde{i}k}$\newline
- $k\leq g$&\raisebox{-2pt}{
- $\begin{array}[t]{@{}c@{}c@{}c@{}c@{}c@{}c@{}c@{}c@{}}
- &gw\widetilde{i}1,..&,gw\widetilde{i}k,&..,gw\widetilde{i}g,G\widetilde{i}1,..&,G\widetilde{i}k,&..,G\widetilde{i}g,P\widetilde{i}1,..,P\widetilde{i}p\\
-<\!& -\,-\,-\    &  ,ium(\widetilde{t}),& -\ -\ -\  &,um(\widetilde{t}),&, -\ -\ -\
-&\!>\longrightarrow \underline{um_{\widetilde{i}.k}(\widetilde{t})}
-% $
-%     \symb{sv}_{u(\widetilde{i}k)}\triangleq
-%     <ium_{\widetilde{i}.k}(\widetilde{t})\otimes
-%     -^{\widetilde{I_P}}\otimes
-%     um_{\widetilde{i}.k}(\widetilde{t})\otimes
-%  -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
-%         k\}}}>\longrightarrow
-%     \underline{um(\widetilde{t})}$
-\end{array}$}  \raisebox{-19pt}{~}  \\
-\hline
-     &{\ERIC{Up gateway}: message m is sent
-  up from a group to its gateway, received by the ium action. The
-  resulting action is visible as the (synchronised) $\underline{um}$ }\\
-\hline
- $(UM)_{\widetilde{i}k}$\newline$k\leq g$
- &\raisebox{-2pt}{$\begin{array}[t]{@{}c@{}c@{}c@{}c@{}c@{}c@{}c@{}c@{}}
- &gw\widetilde{i}1,..&,gw\widetilde{i}k,&..,gw\widetilde{i}g,G\widetilde{i}1,..,G\widetilde{i}g,P\widetilde{i}1,..,P\widetilde{i}p\\
- <\!& -\,-\,-\    &  ,um(\widetilde{t}),& -\ -\ -\   -\ -\ -\
- &\!>\longrightarrow \underline{um(\widetilde{t})}
- \end{array}$}\raisebox{-18pt}{~}\\
-\hline
-$(UM)_{\widetilde{i}k}$\newline$k\leq p$
-&\raisebox{-2pt}{$\begin{array}[t]{@{}c@{}c@{}c@{}c@{}c@{}c@{}c@{}c@{}}
-&gw\widetilde{i}1,..,gw\widetilde{i}g,G\widetilde{i}1,..,,G\widetilde{i}g,P\widetilde{i}1,..&,P\widetilde{i}k,&..,P\widetilde{i}p\\
-<\!& -\ -\ -\      -\ -\ -\ &,um(\widetilde{t}),&   -\, -\, -
-&\!>\longrightarrow \underline{um(\widetilde{t})}
-\end{array}$}\raisebox{-18pt}{~}
- % &
-%$\symb{sv}_{!\widetilde{i}}\triangleq
-%    <um_{\widetilde{i}.k}(\widetilde{t})\otimes
-%    -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\otimes
-%    -^{\widetilde{I_G}}>\longrightarrow
-%    um_{\widetilde{i}.k}(\widetilde{t})$
-\\
-\hline
-     &{\ERIC{Up Message}: message m is sent up from a process
-  or a gateway to the enclosing (= parent) group}\\
-\hline
-
-%% $(BG)_{\widetilde{k}} \ERIC{HB}$ &
-$(HB)_{\widetilde{i}k}$ \newline $k \leq g$
-&\raisebox{-2pt}{$\begin{array}[t]{@{}c@{}c@{}c@{}c@{}c@{}c@{}c@{}c@{}}
-&gw\widetilde{i}1,...&,gw\widetilde{i}k,&..,gw\widetilde{i}g,&G\widetilde{i}1,..,,G\widetilde{i}g&,P\widetilde{i}1,..,
-P\widetilde{i}p \\
-<\!& im(\widetilde{t}), .., im(\widetilde{t}) &, bm(\widetilde{t}),& im(\widetilde{t}),
-..
-im(\widetilde{t}),& -\ -\ -\  &,im(\widetilde{t}),..,im(\widetilde{t})
-&\!>\longrightarrow \underline{bm(\widetilde{t})}
-\end{array}$}\raisebox{-18pt}{~}
-     \\
-\hline
-     &{\ERIC{Horizontal Broadcast}: message m, from a process or a
-  gateway, is broadcast to all its siblings (processes and gateways)
-  inside its group}\\
-\hline\hline\end{tabular}
-\caption{Synchronisation vectors modeling the communication through the HB hierarchy}
-\end{figure}
-
-\end{example}
-
-  \begin{example}\emph{An open-transition.}\label{example:open-trans}
-	After introducing the operational semantics rules, in example
-        \ref{example:deduction-trees}, we shall explain how we 
-	construct this transition using the rules.
-	The transition below corresponds to the application of vector
-        UG at position k=2, and gateway gw2 executing transition
-        $0 \xrightarrow{ium(?tgt2_2)}_{gw2} 2$, storing some address in
-        the state variable $tgt_2$ of gw2..
-
-	\centerline{
-		$\openrule
-		{0 \xrightarrow{a}_{gw2} 2 \\
-			\xrightarrow{b}_{P21}
-			\\ \sm{Pred}_{Root} \\ \emptyset}
-		{\ostate{000} \xrightarrow{v} \ostate{020}}
-		$
-	}
-
-	With the predicates
-
-	$\Pred_{Root} = ( a \!=\! ium(?tgt2_2) \land b\!=\!um(t2) \land b\in
-	Sort_{P21} \land t2 = tgt2_2
-	\land v \!= \! \underline{um(t2)} )  $
-	In the broadcast examples, we do not use assignments and will omit the \Post part of 
-	the open transition.
-\end{example}
-
-\begin{example} \emph{State of a pNet}
-The pNet from Fig. \ref{fig:hb-pnet-graphical} has three leaves (gw1,
-gw2, gw11). So its states will be tuples of length 3,
-e.g. $\triangleleft 102 \triangleright$.
-\end{example}
-
-\begin{example} \emph{Using the operational rules to compute
-    open-transitions}
-  \label{example:deduction-trees}
-
-To build a proof tree, we have to choose one synchronisation vector at
-each instantiation of rule Tr2, and one pLTS transition at each
-instantiation of rule Tr1. Each stage in the proof tree builds one
-open-transition of the corresponding pNet node.  Let us explain in
-detail the first two steps of the
-scenario from Fig. \ref{fig:hb-scenario}:
-
-\begin{figure}[h]
-\centerline{ \includegraphics[width=5cm]{XFIG/HB2} }
-\caption{(open) simplified pNet structure of Hierarchical Broadcast example}
-\label{fig:flattening}
-\end{figure}
-
-\begin{itemize}
-\item Process P21 sends a message towards P111, the combination of sync vectors UM\_21/UG\_2 conveys this message to gateway gw2.
-\item The target address is a relative of gateway gw2, so it
-  broadcasts the message to its siblings using vector HB\_2.
-\end{itemize}
-\end{example}
-
-%% \TODO{but not for local variables of a given pLTS, that MUST keep their
-%%   names through successive use, to keep the dataflow
-%%   information. Still, of course, several instantiations of the same
-%%   pLTS (like gw1, gw2) have distinct local varaibles.}
-
-\paragraph{Building the first transition:}
-
-We use instantiations of the synch vector UM at position 21 (that is a
-hole), and of UG at position 2 (sub-group SG2 in the broadcast hierarchy) gives us :
-\medskip
-
-\noindent
-UM\_21 : $< um(t1), - > \to\!um(t1)$\\
-UG\_2 : $< -, ium(t2), -, -, um(t2) > \longrightarrow \underline{um(t2)}$
-
-\smallskip\noindent
-where the first synch vector (for sub-group SG2) has length 2, and the
-second one (for the root pNet) has length 5. Using once the rule Tr1,
-and twice rule Tr2, we build a proof tree, in which the premisses
-define the behaviour of a gateway pLTS (here
-$0 \xrightarrow{ium(?tgt2_2)}_{gw2} 2$, in which $tgt2_2$ stands for
-the variable $tgt$ of state 2 in gw2), or of a process at a hole
-(e.g. $\xrightarrow{b}_{P21}$ for the process at hole 21).
-The conclusion is an open-transition of the root pNet, with the
-composite state encoding the states of the 3 gateways at the Leaves,
-e.g. $\ostate{000}$.
-
-\begin{mathpar}
-  \inferrule
-      {\inferrule*
-        {0 \xrightarrow{ium(?tgt2_2), True, \emptyset}_{gw2} 2}
-        {\sm{gw2} \models
-             \openrule {0 \xrightarrow{ium(?tgt2_2)}_{gw2} 2}
-                       {\ostate{0} \xrightarrow{ium(?tgt2_2)} \ostate{2} }
-             }
-        \quad
-        \inferrule* [right={[UM\_21]}]
-           {
-             %\sm{fresh}(b_{P21},v_{SG2})
-           }
-           {\sm{SG2} \models
-             \openrule {\xrightarrow{b}_{P21} \quad \sm{Pred}_{UM\_21}}
-                       {\ostate{-} \xrightarrow{v_{SG2}} \ostate{-} }
-             }
-%           \\ {\sm{fresh}(t1,t2,v) }
-           \quad
-           \sm{Pred}_{UG\_2}
-      }
-      {p\_Root
-     \models
-     \openrule
-         {0 \xrightarrow{ium(?tgt2_2)}_{gw2} 2 \\
-           \xrightarrow{b}_{P21}
-          \\ \sm{Pred1}}
-         {\ostate{000} \xrightarrow{v} \ostate{020}}
-      }      ~~ [UG\_2]
-\end{mathpar}
-With:
-
-$Pred_{UM\_21} =  [um(t1)=b \land b\in Sort_{P21} \land um(t1)=v_{SG2}]$
-
-%% $Pred_{UG\_2} = [ium(?t2) = um(t2) \land v_{SG2} = um(t2) ]$
-
-%% $Pred_{Root} = [ium(?t2) = ium(t2) \land b=um(t1) \land
-%%   b\in Sort_{P21} \land v_{SG2}=um(t1) \land v_{SG2} = um(t2)
-%%   \land v = \tau]  $
-
-$Pred_{UG\_2} = [ium(t2) = ium(?tgt2_2) \land um(t2) = v_{SG2} \land
-  v = \underline{um(t2)} ]$
-
-$Pred1 = [Pred_{UM\_21} \land Pred_{UG\_2}]  $
-
-That can be simplified (eliminating the vector local variables and the
-intermediate resulting actions), as: $Pred1 = [b\in Sort_{P21}
-  \land b=um(tgt2_2) \land v=\underline{b} ]  $
-
-%% \TODO{Beware, problem with the ? of ?tgt2: I would prefer having no
-%%   binder (? marker) in the open-automaton predicates, but I do not see
-%% yet how the dataflow will be represented there. OOOOps no more input
-%% var in this transition, t1 is a variable coming from P21.}
-
-\section{Building more transitions of the HB example:}
-\label{appendix:HB-tr2}
-Here we detail the construction of the second transition of our
-scenario:
-
-\begin{mathpar}
-     \openrule
-         {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad
-           2 \xrightarrow{bm(tgt2_2)}_{gw2} 0 \quad
-           \xrightarrow{b}_{P3}
-           \quad Pred_{Root}}
-         {\ostate{020} \xrightarrow{v} \ostate{100}}
-\end{mathpar}
-with
-$Pred_{Root} = [tgt1_1=tgt2_2 \land b=um(tgt2_2) \land
-  b\in Sort_{P3} \land v = \underline{bm(tgt2_2)}]  $
-
-After the first move described in example \ref{example:deduction-trees}, the pLTS of $gw2$ is
-in state 2, ready to emit. We build one
-open-transition for each item in the case statement of its outgoing
-transition; the one we are interested here for our scenario is the
-case where the target address is below $gw1$, corresponding to the
-predicate [$a$=$bm(tgt2_2)$ $\land$ isDirectRelative(2,$tgt2_2$)], and we
-construct the proof tree, reduced here to applications of rule
-Tr1 for transitions of the pLTSs gw1 and gw2, and a single application of rule
-Tr2 for the synch vector HB at index 2:
-
-\medskip\noindent
-HB\_2 : $< im(t3), bm(t3), im(t3) -, - > \longrightarrow \underline{bm(t3)}$
-
-This illustrates the flow of data through sequences of symbolic moves
-of our example: in the first open-transition, the value (address) sent
-by P21 was stored in the state variable $tgt2_2$. In the second
-transition here, synchronisation within the vector HB\_2 yield the
-predicate $tgt1_1=tgt2_2$, and thus transfers the address to the state
-variable $tgt1_1$ in gw1.
-
-\begin{mathpar}
-  \inferrule
-      {\inferrule
-        {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1}
-        { \sm{gw1} \models
-          \openrule
-              {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad \sm{True}}
-              {\ostate{0} \xrightarrow{im(?tgt1_1)} \ostate{1}}
-        }
-        \\
-       \inferrule
-           {2 \xrightarrow{bm(tgt2_2)}_{gw2} 0}
-           { \sm{gw2} \models
-             \openrule
-                 {2 \xrightarrow{bm(tgt2_2)}_{gw2} 0 \quad \sm{Pred}_{gw2}}
-                 {\ostate{2} \xrightarrow{bm(tgt2_2)} \ostate{0}}
-           }
-           \quad Pred_{HB\_2}
-      }
-           {p\_Root
-     \models
-     \openrule
-         {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad
-           2 \xrightarrow{bm(tgt2_2)}_{gw2} 0 \quad
-           \xrightarrow{b}_{P3}
-           \quad Pred2}
-         {\ostate{020} \xrightarrow{v} \ostate{100}}}
-      ~~ [HB\_2]
-\end{mathpar}
-
-$Pred_{gw2} = [\sm{isDirectRelative}(2,tgt2_2)]$
-
-$Pred_{HB\_2} = [im(tgt1_1) = im(t3) \land bm(tgt2_2) = bm(t3) \land b= im(t3) \land b\in Sort_{P3}  \land v = \underline{bm(t3)}]$
-
-$Pred2 = [Pred_{gw2} \land Pred_{HB\_2} ] $
-
-\medskip
-This can be simplified, eliminating the intermediate variable $t3$ of vector
-HB\_2, while keeping the state variables of $gw_1$ and $gw_2$, the
-intermediate $v$ created by Tr2, and the action variable of hole 
-$P3$. This yields finally predicate $Pred2$ :
-
-$Pred2 = [tgt1_1=tgt2_2 \land
-  b\in Sort_{P3} \land b=um(tgt2_2) \land v = \underline{bm(tgt2_2)}]
-$
-
-\medskip
-Alternatively, we could also have elimated variable $v$, and directly
-show the resulting action $\underline{bm(t3)}]$ in the open
-  transition. This is slightly more compact, and maybe more readable,
-  so we shall use this way in the open-automaton below.
-
-\newpage
-
-Below we show the initial transitions of the automaton of our HB
-system. The full open-automaton has 17 states, and we have not
-computed by hand its full set of transitions. This work would be very
-tedious with pen and paper; we are currently developping a software
-tool to this end.
-
-\begin{figure}[h]
-  \includegraphics[width=0.35\linewidth]{XFIG/HB2}
-\end{figure}
-
-In this open-automaton, we have simplified the predicates and
-eliminated the local variables, excepted those from the occurences of
-the pLTS gw1 and gw2, and from the behaviour of holes.
-
-\begin{figure}[h]
-  \includegraphics[width=\linewidth]{XFIG/HB-OpenAut}
-\end{figure}
-\newpage
-
-\begin{eqnarray*}
-OT_1 & = \openrule
-         {0 \xrightarrow{ium(?tgt2)}_{gw2} 2 \quad
-           \xrightarrow{b1}_{P21}
-          \quad P1}
-         {\ostate{000} \xrightarrow{um(tgt2_2)} \ostate{020}}\\
- with & P1 = [b1\in Sort_{P21} \land b1=um(tgt2_2) ]
- \\
-OT_2 & = \openrule
-         {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad
-           2 \xrightarrow{bm(tgt2_2)}_{gw2} 0 \quad
-           \xrightarrow{b2}_{P3}
-           \quad P2}
-         {\ostate{020} \xrightarrow{\underline{bm(tgt2_2)}} \ostate{100}}\\
-         with & P2 = [tgt1_1=tgt2_2 \land IsDirectRelative(2,tgt2_2)
-           \land  b2\in Sort_{P3} \land b2=um(tgt2_2) ]
-         \\
-OT_3 & = \openrule
-         {1 \xrightarrow{dm(tgt1_1)}_{gw1} 0 \quad
-           0 \xrightarrow{im(?tgt11_1)}_{gw11} 1 \quad
-           \xrightarrow{b3}_{P12}
-           \quad P3}
-         {\ostate{100} \xrightarrow{\underline{dm(tgt1_1)}} \ostate{001}}\\
-         with & P3 = [tgt11_1=tgt1_1 \land IsAncestor(1,tgt1_1)
-           \land  b3\in Sort_{P12} \land b3=im(tgt1_1) ]
-         \\
-OT_4 & = \openrule
-         { 1 \xrightarrow{dm(tgt11_1)}_{gw11} 0 \quad
-           \xrightarrow{b4}_{P111}
-           \quad P4}
-         {\ostate{001} \xrightarrow{\underline{dm(tgt11)}} \ostate{000}}\\
- with & P4 = [ b4=im(tgt11_1) \land  b4\in Sort_{P111} \land IsAncestor(11,tgt11_1) ]
-         \\
-OT_5 & = \openrule
-         {1 \xrightarrow{Discard}_{gw1} 0 \quad
-           \quad P5}
-         {\ostate{100} \xrightarrow{\underline{Discard}} \ostate{000}}\\
- with & P5 = [IsDirectRelative(1,tgt1_1) ]
- \\
-OT_6 & = \openrule
-         { 2 \xrightarrow{Discard}_{gw2} 0 \quad
-           \quad P6}
-         {\ostate{020} \xrightarrow{\underline{Discard}} \ostate{000}}\\
- with & P6 = [ IsAncestor(2,tgt2_2) ]
- \\
-OT_7 & = \openrule
-         {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad
-          0 \xrightarrow{im(?tgt2_1)}_{gw2} 1 \quad
-          \xrightarrow{b7}_{P3}\quad
-           \quad P7}
-         {\ostate{000} \xrightarrow{im(?a)} \ostate{110}}\\
- with & P7 = [ tgt1_1 = tgt2_1 = a \land b7\in Sort_{P3} \land b7 = im(?a)  ]
- \\
-OT_8 & = \openrule
-         {2 \xrightarrow{Discard}_{gw2} 0 \quad
-           \quad P8}
-         {\ostate{110} \xrightarrow{Discard} \ostate{100}}\\
- with & P8 = [ IsDirectRelative(2,tgt2_1) ]
-\end{eqnarray*}
+% \newpage
+% \appendix
 
 \end{document}
-
-\section{Discussion on substitution, matching, unification}
-
-\TODO{I think appendices B and C must be removed from the submission
-  (;-). Do we need anything else as an appendix ? Maybe some of the
-  details on Hierarchical Braodcast, when we will deal with the space limit...}
-
-\TODO{this is far from being final... What should we leave here
-  ? a generic definition of what must be part of the Action Algebra
-  definition, substitution, protected variables; and
-  move to other sections the application and examples of these.
-In fact we currently do not use any notion of substitution, nor
-protect variables. Only these predicates, built as sets of equations,
-with a lot of fresh variables...}
-
-\ERIC{[this text in blue is NOT supposed to stay here as such. Just
-    guidelines towards identifying what we need to set up]
-  To define the operational semantics of pNets, we need only two core
-operations on action expressions: specialisation and unification.
-\begin{itemize}
-\item when composing pNets, substituting a pNet for a hole, each action in
-the subnet sort has to match one action of the hole sort, but may be
-more specific (substitution).
-\item when building a proof tree from a synch vector, we collect a
-  number of substitutions from the involved processes, and we have to
-  match them with the action expressions in the vector. The result is
-  a substitution for the variables of the global action, together with
-  a predicate, built from the guards of the controllers and predicates
-  of the subnets.
-\end{itemize}
-In some cases, substitutions are results of full unification between
-action expressions, but in other cases it may be disymetric in the
-sense that some variables can be substituted, and other not. We can
-formalise this in term of ``protected variables'' in the unification,
-opposed to ``input variables'' that can be arbitrarily substituted (=
-can accept any value, like in classical value-passing algebra communication).}
-
-\section{Future papers...}
-
-I removed from here all appendices that were not directly related to this paper.
-They will be providing subjects for future research (internships ?) and future papers, including:
-
-\begin{itemize}
-  \item Is open (strong) bisim compatible with pNet composition operator (as defined in PdP paper) ?
-  \item Is Open-bisimulation compatible with closed bisimulation ?
-    \item Effective algorithm for 1) checking strong bisimulation (given a state partition) 2) computing the coarsest partition (if it exists).
-\item Model-checking Open-Automata:
-This may come to be simpler to define and implement than FH-bisimulation.
-\item FH-Refinement (and maybe even weak bisimulation if we do not find the time and/or space to have it here)
-\item Fulll use-case on Hierarchical Broadcast
-\end{itemize}
-
-\section{Full definition of the HB pNet model}
-\label{Appendix:SynchVectors}
-
-  The table in Fig. \ref{fig:HBvectors} lists the synchronisation
-  vectors used in all 3 algorithms and their variants. The vector
-  naming schema is the following: the first letter encodes the direction
-  of the message: U(p), D(own), H(orizontal); the second letter its
-  type: B(roadcast) G(gateway-group) or M(simple message).
-
-  Additionally, there are 2 special vectors, DIS for (silent) Discard
-  events, and ERR for (visible) Error events.
-
-  Among the 6 basic vectors, 3 of them (UG, DG, UM) are shared by all
-  algorithms, DB is used by Full and hierarchical braodcast, while the
-  last 2, HM and HB are specific to horizontal messages of Unicats and
-  hierarchical brodcast respectively.
-
-  \TODO{missing the variants here...}
-
-\begin{figure}[h!]
-  \label{fig:HBvectors}
-\begin{tabular}{|p{1.6cm}|p{8.8cm}|l|}
-%% \hline\hline
-%% \multicolumn{3}{|l|}{Hierarchical broadcasting}\\
-  \hline
-  \hline
-\multicolumn{3}{|p{12cm}|}{\ERIC{Need a short explanation about notations here: indices, indexed actions to be instanciated to match the terms in the sorts, ...? }}\\
-  \hline
- %% $(UC)_{\widetilde{k}} \ERIC{UG}$ & $
- $(UG)_{\widetilde{k}}$ & $
-     \symb{sv}_{u(\widetilde{i}.k)}\triangleq
-     <?um_{\widetilde{i}.k}(\widetilde{t})\otimes
-     -^{\widetilde{I_P}}\otimes
-     !m_{\widetilde{i}.k}(\widetilde{t})\otimes
-     -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
-         k\}}}>\longrightarrow \tau(
-     m_{\widetilde{i}.k}(\widetilde{t}))$ &
-     $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}$\\
-\hline
-     &\multicolumn{2}{|p{10cm}|}{\ERIC{Up gateway}: message m is sent up from a group to its gateway}\\
-\hline
-%% $(DG)_{\widetilde{k}} \ERIC{DB}$&
-$(DB)_{\widetilde{k}}$&
-$\symb{sv}_{?\widetilde{i}}\triangleq
-     <?m_{\widetilde{i}.k}(\widetilde{t})\otimes
-     -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\otimes
-     -^{\widetilde{I_G}}>\longrightarrow
-     ?dm_{\widetilde{i}}(\widetilde{t})$&$\widetilde{k}=\widetilde{i}.k\in \widetilde{I_{G+P}}$\\
-     \hline
-     &\multicolumn{2}{|p{10cm}|}{\ERIC{Down Broadcast}: a message m received by a group is
-       forwarded (broadcast) to all elements of the group, meaning to
-       all processes and gateways inside.}\\
-\hline
-$(UM)_{\widetilde{k}}$&
-$\symb{sv}_{!\widetilde{i}}\triangleq
-    <!um_{\widetilde{i}.k}(\widetilde{t})\otimes
-    -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\otimes
-    -^{\widetilde{I_G}}>\longrightarrow
-    !um_{\widetilde{i}.k}(\widetilde{t})$ & $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_{G+P}}$\\
-\hline
-     &\multicolumn{2}{|p{10cm}|}{\ERIC{Up Message}: message m is sent up from a process
-  or a gateway to the enclosing (= parent) group}\\
-\hline
-
-%% $(BG)_{\widetilde{k}} \ERIC{HB}$ &
-$(HB)_{\widetilde{k}}$ &
-$\symb{sv}_{b(\widetilde{i}.k)}\triangleq
-    <?m_{\widetilde{i}.j}^{\forall j\in I_K}(\widetilde{t})
-    \otimes !bm_{\widetilde{i}.k}(\widetilde{t})
-    \otimes -^{\widetilde{I_G}}>\longrightarrow \tau( bm(\widetilde{t}))$ &
-    $I_K = \{k/\widetilde{i}.k\in \widetilde{I_{G+P}}\}$, \\ &  &  and
-    $\widetilde{k}=\widetilde{i}.k$ \\
-\hline
-     &\multicolumn{2}{|p{10cm}|}{\ERIC{Horizontal Broadcast}: message m, from a process or a
-  gateway, is broadcast to all its siblings (processes and gateways)
-  inside its group}\\
-
-\hline
-%% $(DC)_{\widetilde{k}} \ERIC{DG}$ &
-$(DG)_{\widetilde{k}}$ &
-$\symb{sv}_{?\widetilde{i}}\triangleq
-     <!dm_{\widetilde{i}.k}(\widetilde{t})\otimes
-     -^{\widetilde{I_P}}\otimes
-     ?dm_{\widetilde{i}.k}(\widetilde{t})\otimes
-     -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}}
-     >\longrightarrow
-     \tau(m_{\widetilde{i}.k}(\widetilde{t}))$,
-%      <?m_{\widetilde{i}.k}^{\forall k\in
-%        I_K}(\widetilde{t})\otimes
-%      -^{\widetilde{I_P}}\otimes -^{\widetilde{I_G}}>\longrightarrow
-     %      ?m_{\widetilde{i}}(\widetilde{t})$
-     & $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}$\\
-
-\hline
-     &\multicolumn{2}{|p{10cm}|}{\ERIC{Down Gateway}: message $m$ is sent down from a gateway
-to the corresponding subgroup; it should then be forwarded inside the
-subgroup, e.g. with $(DM)_{\widetilde{k}}$}\\
-\hline
-%% $(DK)_{\widetilde{k}} \ERIC{DM}$&
-$(DM)_{\widetilde{k}}$&
-$\symb{sv}_{!\widetilde{i}}\triangleq
-    <  ?m_{\widetilde{i}.k}(\widetilde{t})\otimes
-    -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\otimes
-    -^{\widetilde{I_G}}>\longrightarrow ?m_{\widetilde{i}}(\widetilde{t})$
-    & $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_{G+P}}$\\
-\hline
-     &\multicolumn{2}{|p{10cm}|}{\ERIC{Down Message}: Unicast version of (DB): m received
-  by a group is forwarded to one specific element $i.k$ of the group}\\
-\hline
-
-$(HM)_{\widetilde{k}}$&
-$\symb{sv}_{!\widetilde{i}}\triangleq
-   $\\
-\hline
-&\multicolumn{2}{|p{10cm}|}{\ERIC{Horizontal Message}: optimized
-  version of Unicast: message m, from a process or a
-  gateway, is broadcast to one of its its siblings
-  inside the same group}\\
-
-\hline\hline
-$(DIS)_{\widetilde{k}}$&
-     $\symb{sv}_{u(\widetilde{i}.k)}\triangleq
-     <Discard\otimes
-     -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\otimes
-     -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
-         k\}}}>\longrightarrow \tau(DIS)$ &
-     $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}$\\
-\hline
-     &\multicolumn{2}{|p{10cm}|}{\ERIC{DISCARD events} occur in gateways
-  under HB protocol, after receiving a broadcast message which
-  target address is a sibling of the gateway; this message is
-  DISCARDED silently }\\
-\hline
-$(ERR)_{\widetilde{k}}$&
-     $\symb{sv}_{u(\widetilde{i}.k)}\triangleq
-     <Error\otimes
-     -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\otimes
-     -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
-         k\}}}>\longrightarrow Error(\widetilde{k})$ &
-     $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}$\\
-\hline
-     &\multicolumn{2}{|p{10cm}|}{\ERIC{ERROR events} may occur in gateways
-  in 2 cases: either if the message is targeted to a gateway address,
-  that is an error from the emittor (ERR "BadTarget"); or if a gateway
-  receives from its parent or brother a message that should not go
-  within its subgroup, that is a protocol error (ERR "WrongWay").
-  In both cases the ERR message will be transmitted up, for the sake
-  of verification }\\
-\hline\hline\end{tabular}
-\caption{Synchronisation vectors modeling the communication through the HB hierarchy}
-\end{figure}
-
-\section{The  Open Transitions of Broadcasting}
-% \TODO{Min: to modify the tables. }
-
-%%mofication of Table 1
-
-\begin{figure}[h]
-\centerline{ \includegraphics[width=5cm]{XFIG/HB2} }
-\caption{(open) pNet structure of Hierarchical Broadcast example}
-\label{Fig:simpleHBStruct}
-\end{figure}
-
-Figure \ref{Fig:simpleHBStruct} recalls the structure of the pNet tree
-for HB example structure, in which gw1, gw2, gw11 are leaves, and P3,
-P12, P21, P22, P111 are holes.
-
-The following tables list the open-transition derivable from two of
-the first states of the open-automaton of this pNet, including the 2 first
-transitions of our scenario, as explained in section \ref{}.
-
-\noindent
-\begin{tabular}{|p{2.8cm}|p{9cm}|l|}
-\hline\hline
-\multicolumn{3}{|l|}{from state $\ostate{000}$}\\
-\hline
-HB(3) &
-\{gw1, gw2\} \{P3\}  \{$a_{gw1}$=$a_{gw2}$=?m(t), $b_{P3}$=!bm(t'), v=$\tau$,[t=t']\} &
-$\ostate{110}$\\
-\hline
-HB(12)&
-\{gw11\} \{P12\} \{$a_{gw11}$=?m(t), $b_{P12}$=!bm(t'), v=$\tau$, [t=t' ]\} & $\ostate{001}$\\
-\hline
-DB&
-\{gw1, gw2\}\{\}\{$a_{gw1}$=$a_{gw2}$=?m(t), v=?dm(t'),  [t=t']\}&$\ostate{110}$\\
-\hline
-UG(1)(UM(12)) &
-\{gw1\},  \{P12\} \{$a-{gw1}$=?um(t), $b_{P12}$=!um(t'), v=$\tau$, [t=t']\} &
-$\ostate{200}$\\
-\hline
-UG(2)(UM(k)) ${}^{k \in \{21,22\}}$ &
-\{gw2\},  \{Pk\} \{$a_{gw2}$=?um(t), $b_{Pk}$=!um(t'),v=$\tau$, [t=t']\} &
-$\ostate{020}$\\
-\hline
-UG(11)(UM(111)) &
-\{gw11\},  \{P111\} \{$a_{gw11}$=?um(t), $b_{P111}$=!m(t),v=$\tau$, [t=t']\} &
-$\ostate{002}$\\
-\hline\hline
-\end{tabular}
-\vskip 0.3cm
-
-\NOTE{Eric: one transition of the <020> table, from the draft on my white board}
-
-\noindent
-\begin{tabular}{|p{2.8cm}|p{9cm}|l|}
-\hline\hline
-\multicolumn{3}{|l|}{from state <020>}\\
-\hline
-HB(2)&
-\{gw1,gw2\} \{P3\} \{a1=?m(t), a2=!bm(t'), a3=?m(t'), v=tau, [t=t'=t'' $\land$ isDirRel(t,2)]\} & <100>\\
-\hline
-HB(12)&
-\{gw11\} \{P12\} \{a11=?m(t), a12=!bm(t'),  v=tau, [t=t']\} & <021>\\
-\hline
-UG(1)(UM(12)) &
-\{gw1\},  \{P12\} \{a1=?um(t), a12=!um(t'), v=tau,  [t=t'] \} &
-<220>\\
-\hline
-UG(11)(UM(111)) &
-\{gw11\},  \{P111\} \{a11=?um(t), P111=!m(t),v=tau, [t=t']\} &
-<022>\\
-\hline
-ERR(2)&
-\{g2\} \{\} \{a2=Error, v=Error2,[t=2]\}&<000>\\
-\hline
-DiS(2)&
-\{g2\} \{\} \{a2=DIS, v=DIS2,[Ancestor(2, t)]\} &
-<000>\\
-\hline
-\hline
-\end{tabular}
-\vskip 0.3cm
-
-%
-%\noindent
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <1, 1, 0>}\\
-%\hline
-%HB(12)&
-%\{g11\} \{P12\} \{a11=?m(a), a12=!bm(a), v=tau\} & <1, 1, 1>\\
-%\hline
-%UM(k) ${}^{k \in \{3,12\}}$&
-%\{\}\{Pk\}\{ak=!um(a),v=!um(a), isOtherRelative(3, a)\}&<1, 1, 0>\\
-%\hline
-%UM(1)&
-%\{g1\}\{\}\{a1=!um(a),v=!um(a), isOtherRelative(1, a)\}&<0, 1, 0>\\ \hline
-%UM(2)&
-%\{g2\}\{\}\{a2=!um(a),v=!um(a), isOtherRelative(2, a)\}&<1, 0, 0>\\ \hline
-%DG(1)&
-%\{g1\}\{SG1\}\{a1=!dm(a),sg1=?dm(a),v=tau\}&<0, 1, 0>\\ \hline
-%DG(2)&
-%\{g2\}\{SG2\}\{a2=!dm(a),sg2=?dm(a), v=tau\}&<1, 0, 0>\\ \hline
-%
-%DIS(1)&
-%\{g1\} \{\} \{a1=Discard, v=tau\} &
-%<0, 1, 0>\\
-%\hline
-%DIS(2)&
-%\{g2\} \{\} \{a2=Discard, v=tau\} &
-%<1, 0, 0>\\
-%\hline
-%ERR(1)&
-%\{g1\} \{\} \{a1=Error, v=Error1\}, &
-%<0, 1, 0>\\
-%\hline
-%ERR(2)&
-%\{g2\} \{\} \{a2=Error, v=Error2\} &
-%<1, 0, 0>\\
-%\hline
-%UG(11) &
-%\{g11\},  \{SG11\} \{a11=?um(a), sg11=!m(a),v=tau, isOtherRelative(11, a)\} &
-%<1, 1, 2>\\
-%\hline\hline
-%\end{tabular}
-%\vskip 0.3cm
-%\noindent
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <0, 0, 1>}\\
-%\hline
-%HB(3) &
-%\{g1, g2\} \{P3\} \hfill \{a1=a2=?m(a), a3=!bm(a), v=tau\} &
-%<1, 1, 1>\\
-%\hline
-%DB &
-%\{g1, g2\} \{\} \{a1=a2=?m(a), v=?dm(a)\} &
-%<1, 1, 1>\\
-%\hline
-%UG(1) &
-%\{g1\},  \{SG1\} \{a1=?um(a), sg1=!m(a),v=tau, isOtherRelative(1, a)\} &
-%<2, 0, 1>\\
-%\hline
-%UG(2) &
-%\{g2\},  \{SG2\} \{a2=?um(a), sg2=!m(a),v=tau, isOtherRelative(2, a)\} &
-%<0, 2, 1>\\
-%\hline
-%DG(11)  &
-%% $\emptyset$
-%\{g11\} \{SG11\} \{a11=!dm(a),sg11=?dm(a) v=tau,\} & <0, 0, 0>\\
-%\hline
-%
-%DIS11 &
-%\{g11\},\{\}\{a11=Discard, v=tau \}&<0, 0, 0>\\
-% \hline
-% ERR11 &
-%\{g11\},\{\}\{a11=Error, v=Error11 \}&<0, 0, 0>\\
-% \hline\hline
-%\end{tabular}
-%
-%\vskip 0.3cm
-%There is the case of Unicast.
-%\vskip 0.3cm
-%\noindent
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <0, 0, 0>}\\
-%\hline
-%DM1 &
-%\{g1\} \{P3\}  \{a1=?m(a), a3=!m(a), v=tau, isDirectRelative(1,a)\} &
-%<1, 0, 0>\\
-%\hline
-%DM2 &
-%\{g2\} \{P3\}  \{a1=?m(a), a3=!m(a), v=tau, isDirectRelative(2,a)\} &
-%<0, 1, 0>\\
-%\hline
-%DM11 &
-%\{g11\} \{P13\}  \{a11=?m(a), a13=!m(a), v=tau, isDirectRelative(11,a)\} &
-%<0, 0, 1>\\
-%\hline\hline
-%\end{tabular}
-%\vskip 0.3cm
-%\noindent
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <1, 0, 0>}\\
-%\hline
-%DG1 &
-%\{g1\} \{SG1\}  \{a1=!dm(a), sg1=?dm(a), v=tau, isDirectRelative(1,a)\} &
-%<0, 0, 0>\\
-%\hline
-%UM1 &
-%\{g1\} \{\}  \{a1=!um(a), v=!um(a)\} &
-%<0, 0, 0>\\
-%\hline
-%DM2 &
-%\{g2\} \{P3\}  \{a1=?m(a), a3=!m(a), v=tau, isDirectRelative(2,a)\} &
-%<1, 1, 0>\\
-%\hline
-%DM11 &
-%\{g11\} \{P13\}  \{a11=?m(a), a13=!m(a), v=tau, isDirectRelative(11,a)\} &
-%<1, 0, 1>\\
-%\hline
-%ERR(1)&
-%\{g1\} \{\} \{a1=Error, v=tau\} &
-%<0, 0, 0>\\
-%\hline\hline
-%\end{tabular}
-%
-%\vskip 0.3cm
-%
-%\noindent
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <1, 1, 0>}\\
-%\hline
-%DG1 &
-%\{g1\} \{SG1\}  \{a1=!dm(a), sg1=?dm(a), v=tau, isDirectRelative(1,a)\} &
-%<0, 1, 0>\\
-%\hline
-%DG2 &
-%\{g2\} \{SG2\}  \{a2=!dm(a), sg2=?dm(a), v=tau, isDirectRelative(2,a)\} &
-%<1, 0, 0>\\
-%\hline
-%UM1 &
-%\{g1\} \{\}  \{a1=!um(a), v=!um(a)\} &
-%<0, 1, 0>\\
-%\hline
-%UM2 &
-%\{g2\} \{\}  \{a2=!um(a), v=!um(a)\} &
-%<1, 0, 0>\\
-%\hline
-%DM11 &
-%\{g11\} \{P13\}  \{a11=?m(a), a13=!m(a), v=tau, isDirectRelative(11,a)\} &
-%<1, 1, 1>\\
-%\hline
-%ERR(1)&
-%\{g1\} \{\} \{a1=Error, v=tau\} &
-%<0, 1, 0>\\
-%\hline
-%ERR(2)&
-%\{g2\} \{\} \{a2=Error, v=tau\} &
-%<1, 0, 0>\\
-%\hline\hline
-%\end{tabular}
-
-\section{Encapsulating Process arguments}
-In Section \ref{section:processSort} we described the Sort of
-processes in the holes of the herarchical broadcast architecture.
-Here we present a more general solution, using a small pNet as a
-filter encapsulating each of the holes. The filter is in
- charge of relabeling the messages
-from the process depending on their destination, and filtering the
-incoming messages, discarding those received by broadcast, but target
-to other processes. This pNet is shown in the following figure:
-
-\centerline{  \includegraphics[width=0.8\linewidth]{ATG/ProcessFilter}}
-
-This solution has the benefit of allowing any process as an argument
-fitting the hole, without specific constraints on its sort. The price
-is that the pNet structure is a bit more complex, so the open
-transitions and open automata will be bigger also. Moreover the filter
-has states, and this introduces some additional states and
-tau-transitions in the open-automaton.
-
-\section{{pNets Model for Broadcast Flat groups  (BF-pNets):
-    definition}\label{sec:bf-pnets-def}}
-Given a $HB-\pNet$, we can flatten it to decrease the number of layers
-of hierarchical structures using a {\em Flattening Operator}
-$\bowtie$.
-This operation replaces one or several subgroups in the hierarchical
-structure by their content. The corresponding old controllers
-(gateways) won't exist after flattening. Fig. \ref{fig:flattening}
-shows the flattening operator at work, on 2 subgroups SG1 and SG2, at the
-toplevel of the example.
-\begin{definition}[Flattening Operation]
-Assume a $HB-\pNet$ has the structure:
-$\mylangle gw_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}},  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, sg_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}}\myrangle$
-where
-$ \forall \widetilde{g}\in \widetilde{I_G}$,  the $sg_{\widetilde{g}}$ has the $HB-\pNet$ structure:
- $\mylangle gw_{\widetilde{g}\cdot g_i}^{g_i\in I_{G_{\widetilde{g}}}},  pc_{\widetilde{g}\cdot p_j}^{p_j\in I_{P_{\widetilde{g}}}}, sg_{\widetilde{g}\cdot g_i}^{g_i\in I_{G_{\widetilde{g}}}}\myrangle $.
- \medskip
-
- Then
-the flattening map
-$\bowtie_{\widetilde{g}}: HB-pNets\longrightarrow HB-pNets$, where\\
-
- \medskip
- $\bowtie_{\widetilde{g}}(HB-\pNet)\triangleq \mylangle gw_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g}\}}, gw_{\widetilde{g}\cdot g_i}^{g_i\in I_{G_{\widetilde{g}}}},  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, pc_{\widetilde{g}.\cdot p_j}^{p_j\in I_{P_{\widetilde{g}}}},sg_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g}\}}, sg_{\widetilde{g}\cdot g_i}^{g_i\in I_{G_{\widetilde{g}}}}\myrangle$.
- \medskip
-
-The flattening operator shows one subgroup $sg_{\widetilde{g}}$ can be flatten to one hole of his father group which is linked the gateway $gw_{\widetilde{g}}$, the gateways,the processes ,and the holes of $sg_{\widetilde{g}}$ become the gateways, the processes, and the holes of his father group instead of itself and the gateway that it is linked.
-
-Actually, for any subgroup (hole) of the group, the flattening operation can be done in parallel without the order.
-We denote that  $\bowtie_{\widetilde{I_G}}\triangleq\Sigma_{\widetilde{g}\in{\widetilde{I_G}}}\bowtie_{\widetilde{g}}$, where:
-
- $\bowtie_{\widetilde{I_G}}(HB-\pNet)\triangleq \mylangle  gw_{\widetilde{g}\cdot g_i}^{\widetilde{g}\in \widetilde{I_G}, g_i\in I_{G_{\widetilde{g}}}},  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, pc_{\widetilde{g}\cdot p_j}^{\widetilde{g}\in \widetilde{I_G}, p_j\in I_{P_{\widetilde{g}}}}, sg_{\widetilde{g}\cdot g_i}^{\widetilde{g}\in \widetilde{I_G}, g_i\in I_{G_{\widetilde{g}}}}\myrangle$.
-\end{definition}
-
-Especially, if some $\widetilde{g_0}\in{\widetilde{I_G}}$, the $sg_{\widetilde{g_0}}$ has the $HB-\pNet_{\widetilde{g_0}}$ structure: $\mylangle -,  pc_{\widetilde{g_0}\cdot p_j}^{p_j\in I_{P_{\widetilde{g}}}}, -\myrangle$.
-
- $\bowtie_{\widetilde{g_0}}(HB-\pNet)\triangleq \mylangle gw_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g}\}},   pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, pc_{\widetilde{g_0}\cdot p_j}^{ p_j\in I_{P_{\widetilde{g}}}},sg_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g}\}}\myrangle$.
-
-% If all the subgroups $sg_{\widetilde{g}}$ have the similar structures to $sg_{\widetilde{g_0}}$, $\forall \widetilde{g}\in \widetilde{I_G}$, we have
-%
-%  $\bowtie_{\widetilde{I_G}}(HB-\pNet)\triangleq \mylangle -,  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, pc_{\widetilde{g}\cdot p_j}^{\widetilde{g}\in \widetilde{I_G}, p_j\in I_{P_{\widetilde{g}}}}, -\myrangle$.
-
-\medskip
-%
-%\begin{definition}[Equivenlence]
-%\NOTE{The equivalence between $HB-\pNet$ and $BF-\pNet$ should be defined.}
-%\end{definition}
-
- Let $HB-\pNet$ node have the structure $\mylangle gw_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}},  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, sg_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}}\myrangle$, with some subgroup the $sg_{\widetilde{g_0}}$ who has the  structure:
- $\mylangle gw_{\widetilde{g_0}\cdot g_i}^{g_i\in I_{G_{\widetilde{g_0}}}},  pc_{\widetilde{g_0}\cdot p_j}^{p_j\in I_{P_{\widetilde{g_0}}}}, sg_{\widetilde{g_0}\cdot g_i}^{g_i\in I_{G_{\widetilde{g_0}}}}\myrangle $, has one corresponding flatten broadcast open $\pNet$ by the flattening operator $\bowtie_{\widetilde{g_0}}$, i.e.
-$\mylangle gw_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g_0}\}}, gw_{\widetilde{g_0}\cdot g_i}^{g_i\in I_{G_{\widetilde{g}}}},  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, pc_{\widetilde{g_0}.\cdot p_j}^{p_j\in I_{P_{\widetilde{g}}}},sg_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g_0}\}}, sg_{\widetilde{g_0}\cdot g_i}^{g_i\in I_{G_{\widetilde{g}}}}\myrangle$.
-
-\section{Sketch of the proof}
-\label{sec:proof-sketch}
-
-In this section we will describe a proof of equivalence between a HB
-pNet node (seen as an open pNet), with the corresponding flatten
-broadcast open pNet. From this equivalence, it is easy to derive the
-equivalence of a fully instantiated (= closed) HB-pNet structure with
-the corresponding flatten pNet.
-
-\begin{theorem}
-Any $\mathcal{HB-\pNet}$ node is FH-bisimular to the corresponding $\mathcal{BF-\pNet}$ node by the flatting operator $\bowtie$, that is, \\
-$\mylangle gw_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}},  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, sg_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g_0}\}},\mylangle gw_{\widetilde{g_0}\cdot g_i}^{g_i\in I_{G_{\widetilde{g_0}}}},  pc_{\widetilde{g_0}\cdot p_j}^{p_j\in I_{P_{\widetilde{g_0}}}}, sg_{\widetilde{g_0}\cdot g_i}^{g_i\in I_{G_{\widetilde{g_0}}}}\myrangle  \myrangle \approx_{FH} \\ \mylangle gw_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g_0}\}}, gw_{\widetilde{g_0}\cdot g_i}^{g_i\in I_{G_{\widetilde{g}}}},  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, pc_{\widetilde{g_0}.\cdot p_j}^{p_j\in I_{P_{\widetilde{g}}}},sg_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g_0}\}}, sg_{\widetilde{g_0}\cdot g_i}^{g_i\in I_{G_{\widetilde{g}}}}\myrangle$.
-\end{theorem}
-
-The sketch we give here considers one particular pNet node, with 2
-subgroups, and a specific number of processes in each root- and sub-
-groups. Also we make some hypotheses on the sorts of the processes.
-Clearly the full proof will have to deal with generalisations of this
-particular case.
-
-\begin{figure}[h]
-\includegraphics[width=6cm]{XFIG/HB2}
-\hspace{1cm}
-\includegraphics[width=5cm]{XFIG/B2}
-\caption{(open) pNet structure of Hierarchical and flat example}
-\label{fig:flattening}
-\end{figure}
-
-\paragraph{More precisely:}
-
-\paragraph{Principles of the proof:}
-
-We start from the hierarchical pNet, build all its possible behaviours
-(building proof trees from possible synch vectors of the pNet, and
-possible actions in the sorts of holes), then show that there is a
-corresponding behaviour for the flat pNet. Similar method is then
-applied in the symetrical direction.
-
-A state of the hierarchical pNet will be a hierarchical vector of
-``states'', in which we shall represent the state of a controller with
-its name followed by the state index (gateways have only two states,
-numered \{0,1\}); and state of holes with simply the name of the hole.
-To keep state structure compact and keep readability, we show pLTS
-states by their number, subscripted by the name of the gateway. For
-processes and sub-groups, that have no states, we only show their name.
-%
-%
-%
-%\noindent
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <0, 0, 0>}\\
-%\hline
-%Bm(3) &
-%\{g1, g2\} \{P3\} \hfill \{a1=a2=?bm(a), a3=!m(a), v=tau\} &
-%<1, 1, 0>\\
-%\hline
-%Bm(12)&
-%\{g11\} \{P12,P13\} \{a11=a13=?um(a), a12=!m(a), v=tau\} & <0, 0, 1>\\
-%\hline
-%Bm(13)&
-%\{g11\} \{P12,P13\} \{a11=a12=?um(a), a13=!m(a), v=tau\} & <0, 0, 1>\\
-%\hline
-%DA &
-%\{g1, g2\} \{P3\} \{a1=a2=a3=?bm(a), v=?m(a)\} &
-%<1, 1, 0>\\
-%\hline
-%Um(1) &
-%\{g1\},  \{SG1\} \{a1=?bm(a), sg1=!m(a),v=tau, isOtherRelative(1, a)\} &
-%<2, 0, 0>\\
-%\hline
-%Um(2) &
-%\{g2\},  \{SG2\} \{a2=?bm(a), sg2=!m(a),v=tau, isOtherRelative(2, a)\} &
-%<0, 2, 0>\\
-%\hline
-%Um(11) &
-%\{g11\},  \{SG11\} \{a11=?bm(a), sg11=!m(a),v=tau, isOtherRelative(11, a)\} &
-%<0, 0, 2>\\
-%\hline
-%UA(k) ${}^{k \in \{3,12,13,21\}}$ &
-%% $\emptyset$
-%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <0, 0, 0>\\
-%\hline\hline
-%\end{tabular}
-%
-%\noindent
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <1, 1, 0>}\\
-%\hline
-%Bm(12)&
-%\{g11\} \{P12,P13\} \{a11=a13=?um(a), a12=!m(a), v=tau\} & <1, 1, 1>\\
-%\hline
-%Bm(13)&
-%\{g11\} \{P12,P13\} \{a11=a12=?um(a), a13=!m(a), v=tau\} & <1, 1, 1>\\
-%\hline
-%UA(3)&
-%\{\}\{P3\}\{a3=!um(a),v=!m(a), isOtherRelative(3, a)\}&<1, 1, 0>\\
-%\hline
-%UA(1)&
-%\{g1\}\{\}\{a1=!um(a),v=!m(a), isOtherRelative(1, a)\}&<0, 1, 0>\\ \hline
-%UA(2)&
-%\{g2\}\{\}\{a2=!um(a),v=!m(a), isOtherRelative(2, a)\}&<1, 0, 0>\\ \hline
-%$Dm_1(DA_1)$ &
-%\{g1,g11\}\{SG1,P12,P13\}\{a1=!dm(a), sg1=?m(a),a11=a12=a13=?bm(a), v=tau, isDirectRelative(1,a)\}&<0, 1, 1>\\ \hline
-%$Dm_2(DA_2)$ &
-%\{g2\}\{SG2,P21\}\{a2=!dm(a), sg2=?m(a), a21=?bm(a), v=tau, isDirectRelative(2,a)\}&<1, 0, 0>\\ \hline
-%DISCARD(1)&
-%\{g1\} \{\} \{a11DISCARD, v=tau\} &
-%<0, 1, 0>\\
-%\hline
-%DISCARD(2)&
-%\{g2\} \{\} \{a2=DISCARD, v=tau\} &
-%<1, 0, 0>\\
-%\hline
-%Um(11) &
-%\{g11\},  \{SG11\} \{a11=?bm(a), sg11=!m(a),v=tau, isOtherRelative(11, a)\} &
-%<1, 1, 2>\\
-%\hline\hline
-%\end{tabular}
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <0, 0, 1>}\\
-%\hline
-%Bm(3) &
-%\{g1, g2\} \{P3\} \hfill \{a1=a2=?bm(a), a3=!m(a), v=tau\} &
-%<1, 1, 1>\\
-%\hline
-%DA &
-%\{g1, g2\} \{P3\} \{a1=a2=a3=?bm(a), v=?m(a)\} &
-%<1, 1, 1>\\
-%\hline
-%Um(1) &
-%\{g1\},  \{SG1\} \{a1=?bm(a), sg1=!m(a),v=tau, isOtherRelative(1, a)\} &
-%<2, 0, 1>\\
-%\hline
-%Um(2) &
-%\{g2\},  \{SG2\} \{a2=?bm(a), sg2=!m(a),v=tau, isOtherRelative(2, a)\} &
-%<0, 2, 1>\\
-%\hline
-%UA(k) ${}^{k \in \{3,12,13,21\}}$ &
-%% $\emptyset$
-%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <0, 0, 1>\\
-%\hline
-%UA(11)  &
-%% $\emptyset$
-%\{g11\} \{\} \{a11=!um(a), v=!m(a)\} & <0, 0, 0>\\
-%\hline
-%Dm(11)&
-%\{g11\},\{SG1\},\{a11=!dm(a),sg11=?m(a), v=tau, isDirectRelative(11,a)\}&<0, 0, 0>\\
-%\hline
-%DISCARD &
-%\{g11\},\{\}\{a11=DISCARD, v=tau, isOtherRelative(11,a) \}&<0, 0, 0>\\ \hline\hline
-%\end{tabular}
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <2, 0, 0>}\\
-%\hline
-%Bm(12) &
-%\{g11\} \{P12,P13\}  \{a11=a12=?bm(a), a13=!m(a), v=tau\} &
-%<2, 0, 1>\\
-%\hline
-%Bm(13) &
-%\{g11\} \{P12,P13\}  \{a11=a13=?bm(a), a12=!m(a), v=tau\} &
-%<2, 0, 1>\\
-%\hline
-%Bm(1) &
-%\{g1,g2\} \{P3\}  \{a2=a3=?bm(a), a1=!m(a), v=tau\} &
-%<0, 1, 0>\\
-%\hline
-%Um(2) &
-%\{g2\},  \{SG2\} \{a2=?bm(a), sg2=!m(a),v=tau, isOtherRelative(2, a)\} &
-%<2, 2, 0>\\
-%\hline
-%UA(k) ${}^{k \in \{3,12,13,21\}}$ &
-%% $\emptyset$
-%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <2, 0, 0>\\
-%\hline
-%UA(1)  &
-%% $\emptyset$
-%\{g1\} \{\} \{a1=!um(a), v=!m(a)\} & <0, 0, 0>\\
-%\hline
-%Um(11)&
-%\{g11\}\{SG11\}\{a11=?um(a), sg11=!m(a), v=tau, isOtherRelative(11,a)\}&<2, 0, 2>\\
-%\hline
-%DISCARD(1) &
-%\{g1\},\{\},\{a1=DISCARD, v=tau, isDirectRelative(1,a)\}&<0, 0, 0>\\
-%\hline\hline
-%\end{tabular}
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <0, 2, 0>}\\
-%\hline
-%Bm(12) &
-%\{g11\} \{P12,P13\}  \{a11=a12=?bm(a), a13=!m(a), v=tau\} &
-%<0, 2, 1>\\
-%\hline
-%Bm(13) &
-%\{g11\} \{P12,P13\}  \{a11=a13=?bm(a), a12=!m(a), v=tau\} &
-%<0, 2, 1>\\
-%\hline
-%Bm(2) &
-%\{g1,g2\} \{P3\}  \{a1=a3=?bm(a), a2=!m(a), v=tau\} &
-%<1, 0, 0>\\
-%\hline
-%Um(1) &
-%\{g1\},  \{SG1\} \{a1=?bm(a), sg1=!m(a),v=tau, isOtherRelative(2, a)\} &
-%<2, 2, 0>\\
-%\hline
-%UA(k) ${}^{k \in \{3,12,13\}}$ &
-%% $\emptyset$
-%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <0, 2, 0>\\
-%\hline
-%UA(2)  &
-%% $\emptyset$
-%\{g2\} \{\} \{a2=!um(a), v=!m(a)\} & <0, 0, 0>\\
-%\hline
-%DISCARD(2)&
-%\{g2\},\{\},\{a2=DISCARD, v=tau, isDirectRelative(2,a)\}&<0, 0, 0>\\
-%\hline
-%Um(11) &
-%\{g11\},\{SG11\}\{a11=?um(a), sg11=!m(a), v=tau, isOtherReltive(11, a) \}&<0, 2, 2>\\ \hline\hline
-%\end{tabular}
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <0, 0, 2>}\\
-%\hline
-%Bm(3) &
-%\{g1, g2\} \{P3\} \hfill \{a1=a2=?bm(a), a3=!m(a), v=tau\} &
-%<1, 1, 2>\\
-%\hline
-%DA &
-%\{g1, g2\} \{P3\} \{a1=a2=a3=?bm(a), v=?m(a)\} &
-%<1, 1, 2>\\
-%\hline
-%Um(1) &
-%\{g1\},  \{SG1\} \{a1=?bm(a), sg1=!m(a),v=tau, isOtherRelative(1, a)\} &
-%<2, 0, 2>\\
-%\hline
-%Um(2) &
-%\{g2\},  \{SG2\} \{a2=?bm(a), sg2=!m(a),v=tau, isOtherRelative(2, a)\} &
-%<0, 2, 2>\\
-%\hline
-%UA(k) ${}^{k \in \{3,12,13,21\}}$ &
-%% $\emptyset$
-%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <0, 0, 2>\\
-%\hline
-%UA(11)  &
-%% $\emptyset$
-%\{g11\} \{\} \{a11=!um(a), v=!m(a)\} & <0, 0, 0>\\
-%\hline
-%Bm(11)&
-%\{g11\},\{P12,P13\},\{a11=!m(a),a12=a13=?bm(a), v=tau, \}&<0, 0, 0>\\
-%\hline
-%DISCARD(11)&
-%\{g11\},\{\}\{a11=DISCARD, v=tau, isDirectRelative(11,a) \}&<0, 0, 0>\\ \hline\hline
-%\end{tabular}
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <1, 1, 1>}\\
-%\hline
-%UA(1)&
-%\{g1\}\{\}\{a1=!um(a),v=!m(a), isOtherRelative(1, a)\}&<0, 1, 1>\\
-%\hline
-%UA(2)&
-%\{g2\}\{\}\{a2=!um(a),v=!m(a), isOtherRelative(2, a)\}&<1, 0, 1>\\
-%\hline
-%UA(3)&
-%\{\}\{P3\}\{a3=!um(a),v=!m(a), isOtherRelative(3, a)\}&<1, 1, 1>\\
-%\hline
-%Dm(11)&
-%\{g11\}\{SG11\}\{a11=!dm(a), sg11=?m(a), v=tau, isDirectRelative(11,a)\}&<1, 1, 0>\\ \hline
-%$Dm_2(DA_2)$ &
-%\{g2\}\{SG2,P21\}\{a2=!dm(a), sg2=?m(a),a21=?bm(a), v=tau, isDirectRelative(2,a)\}&<1, 0, 1>\\ \hline
-%DISCARD(1)&
-%\{g1\} \{\} \{a1=DISCARD, v=tau, isOtherRelative(1,a)\} &
-%<0, 1, 1>\\
-%\hline
-%DISCARD(2)&
-%\{g2\} \{\} \{a2=DISCARD, v=tau, isOtherRelative(2,a)\} &
-%<1, 0, 1>\\
-%\hline
-%DISCARD(11)&
-%\{g11\} \{\} \{a11=DISCARD, v=tau, isOtherRelative(11,a)\} &
-%<1, 1, 0>\\
-%\hline\hline
-%\end{tabular}
-%\begin{tabular}{|p{2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <0, 1, 0>}\\
-%\hline
-%Bm(12) &
-%\{g11\} \{P12,P13\}  \{a11=a12=?bm(a), a13=!m(a), v=tau\} &
-%<0, 1, 1>\\
-%\hline
-%Bm(13) &
-%\{g11\} \{P12,P13\}  \{a11=a13=?bm(a), a12=!m(a), v=tau\} &
-%<0, 1, 1>\\
-%\hline
-%Um(1) &
-%\{g1\},  \{SG1\} \{a1=?um(a), sg1=!m(a),v=tau, isOtherRelative(1, a)\} &
-%<2, 1, 0>\\
-%\hline
-%Um(11) &
-%\{g11\},  \{SG11\} \{a11=?um(a), sg1=!m(a),v=tau, isOtherRelative(11, a)\} &
-%<0, 1, 2>\\
-%\hline
-%UA(k) ${}^{k \in \{3,12,13\}}$ &
-%% $\emptyset$
-%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <0, 1, 0>\\
-%\hline
-%UA(2)  &
-%% $\emptyset$
-%\{g2\} \{\} \{a2=!um(a), v=!m(a)\} & <0, 0, 0>\\
-%\hline
-%$Dm_2(DA_2)$ &
-%\{g2\},\{SG2,P21\},\{a2=!dm(a),sg2=?m(a),a21=?bm(a) v=tau, isDirectRelative(2,a)\}&<0, 0, 0>\\
-%\hline
-%DISCARD(2) &
-%\{g2\},\{\}\{a2=DISCARD, v=tau, isOtherRelative(2,a) \}&<0, 0, 0>\\ \hline\hline
-%\end{tabular}
-%\begin{tabular}{|p{2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <1, 0, 0>}\\
-%\hline
-%Bm(12) &
-%\{g11\} \{P12,P13\}  \{a11=a12=?bm(a), a13=!m(a), v=tau\} &
-%<1, 0, 1>\\
-%\hline
-%Bm(13) &
-%\{g11\} \{P12,P13\}  \{a11=a13=?bm(a), a12=!m(a), v=tau\} &
-%<1, 0, 1>\\
-%\hline
-%DISCARD &
-%\{g1\} \{\}  \{a1=DISCARD),  v=tau, isOtherRelative(1,a)\} &
-%<0, 0, 0>\\
-%\hline
-%Um(2) &
-%\{g2\},  \{SG2\} \{a2=?bm(a), sg2=!m(a),v=tau, isOtherRelative(2, a)\} &
-%<1, 2, 0>\\
-%\hline
-%Um(11) &
-%\{g11\},  \{SG11\} \{a11=?bm(a), sg11=!m(a),v=tau, isOtherRelative(11, a)\} &
-%<1, 0, 2>\\
-%\hline
-%UA(k) ${}^{k \in \{3,21\}}$ &
-%% $\emptyset$
-%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <1, 0, 0>\\
-%\hline
-%UA(1)  &
-%% $\emptyset$
-%\{g1\} \{\} \{a1=!um(a), v=!m(a)\} & <0, 0, 0>\\
-%\hline
-%$Dm_1(DA_1)$ &
-%\{g1,g11\},\{SG1, P12, P13\},\{a1=!dm(a),sg11=?m(a), a11=a12=a13=?bm(a), v=tau, isDirectRelative(1,a)\}&<0, 0, 0>\\
-%\hline
-%DA(1) &
-%\{g11\},\{P12,P13\}\{a11=a12=a13=?bm(a), v=?m(a) \}&<1, 0, 0>\\ \hline\hline
-%\end{tabular}
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <0, 1, 1>}\\
-%\hline
-%DISCARD(2) &
-%\{g2\} \{\}  \{a2=DISCARD),  v=tau, isOtherRelative(2,a)\} &
-%<0, 0, 1>\\
-%\hline
-%DISCARD(11) &
-%\{g11\} \{\}  \{a11=DISCARD),  v=tau, isOtherRelative(11,a)\} &
-%<0, 1, 0>\\
-%\hline
-%Um(1) &
-%\{g1\},  \{SG1\} \{a1=?um(a), sg1=!m(a),v=tau, isOtherRelative(1, a)\} &
-%<2, 1, 1>\\
-%\hline
-%UA(k) ${}^{k \in \{3,12,13\}}$ &
-%% $\emptyset$
-%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <0, 1, 1>\\
-%\hline
-%UA(2)  &
-%% $\emptyset$
-%\{g2\} \{\} \{a2=!um(a), v=!m(a)\} & <0, 0, 1>\\
-%\hline
-%$Dm_2(DA_2)$&
-%\{g2\},\{SG2,P21\},\{a2=!dm(a),sg2=?m(a),a21=?bm(a), v=tau, isDirectRelative(2,a)\}&<0, 0, 1>\\
-%\hline
-%Dm(11)&
-%\{g11\},\{SG11\},\{a11=!dm(a),sg11=?m(a), v=tau, isDirectRelative(11,a)\}&<0, 1, 0>\\
-%\hline\hline
-%\end{tabular}
-%
-%\noindent
-%\begin{tabular}{|p{2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <0>}\\
-%\hline
-%Bm(3) &
-%\{g11\} \{P3,P12,P13,P21\} \hfill \{a11=a12=a13=a21=?bm(a), a3=!m(a), v=tau\} &
-%<1>\\
-%\hline
-%\multicolumn{2}{|l|}{Bm(12,13,21) are similar} & <1>\\
-%\hline
-%Um(11) &
-%\{g11\} \{SG11\} \{a11=?um(a), sg11=!m(a), v=tau\} & <2>\\
-%\hline
-%DA &
-%\{g11\} \{P3,P12,P13,P21\} \{a3=a11=a12=a13=a21=?bm(a), v=?m(a)\} &
-%<1>\\
-%\hline
-%UA(k) ${}^{k \in \{3,12,13,21\}}$ &
-%% $\emptyset$
-%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <0>\\
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <1>}\\
-%\hline
-%DISCARD&
-%{g11} \{\} \hfill \{a11=DISCARD, v=tau, isDirectRelative(11,a)\} &
-%<0>\\
-%\hline
-%UA(11)& \{g11\} \{\} \{a11=!um(a), v=!m(a), isOtherRelative(11,a)\}& <0>\\
-%\hline
-%UA(k) ${}^{k \in \{3,12,13,21\}}$ &
-%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <1>\\
-%\hline
-%Dm(11)& \{g11\} \{SG11\} \{a11=!dm(a), sg11=?dm(a), v=tau, isAncestor(11,a)\} & <0>\\
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <2>}\\
-%\hline
-%Bm(11) &
-%{g11} \{P3,P12,P13,P21\} \hfill \{a11=!bm(a), a3=a12=a13=a21=?bm(a),
-%v=tau, isDirectRelative(11,a)\} & <0>\\
-%\hline
-%UA(11) &
-%{g11} \{\} \hfill \{a11=!um(a),
-%v=!m(a), isOtherRelative(11,a)\} & <0>\\
-%\hline
-%UA(k) ${}^{k \in \{3,12,13,21\}}$ &
-%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <2>\\
-%\hline
-%DISCARD &
-%{g11} \{\} \hfill \{a11=DISCARD, v=tau, isAncestor(11,a)\} & <0>\\
-%\hline\hline
-%
-%\end{tabular}
-
-\section{Open-bisimulation is compatible with closed bisimulation ?}
-
-\TODO{Underneath is the rules of the closed semantics. Not sure we
-  should keep them here, but we mentionned we should have a proof of
-  the relation between the 2 semantics... In an extended version I
-  suppose (;-)}
-
-\begin{mathpar}
-    \inferrule{\phi,\phi',\phi''\!\in\!\Phi\\s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in J}\rangle} s'\in \to\\\\
-      \phi'\!=\!\phi\!+\!\{x'_i\!\to\!V_i|x'_i\!\in\!\iv(\alpha)\land V_i\!\in\!\mathcal{D}\} \\
-      e_b\phi'\!=\!\symb{True} \\ \phi''\!=\!\phi'+\{x_j\!\to\! e_j\phi'|j\!\in\! J\}}
-    {(s,\phi) \xrightarrow{\alpha\phi'} (s',\phi'') \in\llbracket\mylangle S,s_0,
-      \to\myrangle\rrbracket_\Phi}~~{\bf Tr1}
-%         \end{mathpar}
-% \begin{mathpar}
-
-    \inferrule {\phi,\phi'\in\Phi\\ \alpha_l^{l\in L} \to \alpha \in \overline{\symb{SV}}\\\forall i\in I\phi\setminus
-      L\phi.\,s'_i=s_i
-      \\ %\iv(\alpha)=(x_k)^{k\in K}\\\\
-      \forall l\in L\phi.\,\phi_l\in\Phi\land s_l \xrightarrow{\alpha_l\phi_l} s'_l\in\llbracket\pNet_l\rrbracket_{\Phi}\\\phi'=\phi+\uplus_{l\in L\phi} \phi_{l} }
-{\triangleleft s_i^{i\in I\phi}\triangleright \xrightarrow{\alpha\phi'} \triangleleft{s'_i}^{i\in
-        I\phi'}\triangleright  \in \llbracket\mylangle \pNet_i^{i\in I},\emptyset,\overline{\symb{SV}}\myrangle\rrbracket_\Phi}~~{\bf Tr2}
-\end{mathpar}
-
-\section{Model Checking open-automata}
- \TODO{The following is about the logic formula}
-
-We want to check (and prove) properties on open pNets, using
-model-checking techniques on their open-automata. The properties will be
-expressed in any version of (action-based) branching temporal logics,
-in which we have to add constructs for quantification over the holes
-and/or leaves involved in a transition. For simplicity of the
-definition, we could choose here ACTL \cite{ACTL1990,ACTL1993} or ACTL*
-\cite{DeNicolaVaandrager95}, or the modal $\mu$-calculus
-\cite{Koz83}. Instead, for its easiness of
-expression of value-passing calculi properties, we use here the {\em
-  Model Checking Language} MCL \cite{MateescuFM2008}
-
-\begin{definition}[FH-ACTL ] The logic formula of ACTL (adding  syntax
-  for quantifying over open \pNet s : $\forall t\in {\cal{P}}, H_i \xrightarrow{a} H_i^\prime $)
-\end{definition}
-
- \begin{definition}[FH-satisfiability] Suppose that $F$ is an open
-   \pNet\ expression, and $\phi$ is a temporal logic formula, we say
-   $F$ satisfies the $\phi$, denoted as   $F\vDash_{FH} \phi$,  if
- \end{definition}
-
- In a quite standard way, we define the model checking problem as
- satisfiability of an FH-ACTL formula in a state of a FH-automaton.
-The specificity is that the model (FH-automaton) transitions include
-hypotheses about which holes are involved and predicates about their
-behaviours.
-
- \begin{definition}[The Open MC problem]
- \end{definition}
-
- \section{refinement}
- \begin{definition}[FH-refinement] FH-refinement relation $\ll$ is a
-   binary relation in between open \pNet \ expressions iff for any
-   open \pNet \ expressions $E$ and $F$, $E\ll F$, we have the
-   follows:
- \begin{itemize}
- \item $\P(E)=\P(F)$;
- \item  For any  $E\xrightarrow{S, Pred, a} E'$ based on one open transition $(S, Pred, E')$ for $F$,   there exist a set indexed by $\{j\in J\}$ of transitions  $\{ F\xrightarrow{S_j, Pred_j, a\tau^\star} F_j^\prime| a=a' up\ to\ \alpha-conversation\}$  such that $\forall j\in J, S\subset S_j,  E'\ll F_j'$ and $Pred=\cup_j Pred_j$.
- \end{itemize}
- \end{definition}
- \begin{definition}[Weak FH-refinement] FH-refinement relation $\ll$ is a binary relation in between open \pNet \ expressions iff for any open \pNet \ expressions $E$ and $F$, $E\ll F$, we have the follows:
- \begin{itemize}
- \item $\P(F)=\P(E)$;
- \item  For any  $E\xrightarrow{S, Pred, a} E'$ based on one open transition $(S, Pred, E')$ for $E$,   there exist a set indexed by $\{j\in J\}$ of transitions  $\{ F\xRightarrow{(\uplus_i S_i)_j, (\cap_i Pred_i)_j, \tau^\star a'\tau^\star} F_j^\prime| F\xrightarrow{S_i, Pred_i, a'/\tau} F_i, a=a' up \ to \ \alpha-conversation\}$  such that $\forall j\in J, S=(\uplus_i S_i)_j, E'\ll F_j^\prime$  and $Pred \subseteq \cup_j(\cap_i Pred_i)_j$.
- \end{itemize}
- \end{definition}
-
- \begin{theorem} Suppose that two \pNet s expressions $E$ and $F$ where $E$ is strong FH-bisimilar to $F$.
-For any temporal logic formula $\phi$,  if $E\vDash_{FH}\phi$, then we have $F\vDash_{FH} \phi$.
- \end{theorem}
-
-  \section{pNets Model for Hierarchical Broadcast groups  (HB-pNets): definition}\label{sec:b-pnets-def}
-
-In this section, we give the formal model for the broadcast type of
-hierarchical groups using our open parameterised networks (pNets).
-
-Hierarchical Broadcast (HB) is a way of implementing broadcasting
-algorithms within a large set of processes, with better performances
-and scalability. There have been many proposals for hierarchical
-broadcast algorithms (cite...), most of them focussing on specific
-architectures or features (in particular fault tolerance), and on
-performance analysis. Very few have given a formal description of the
-algorithm, allowing to reason about their safety properties.
-
-We give here the description of one simple HB algorithm, extracted
-from\cite{Taguchi03}, but without fault
-tolerance in a first step. For the formal description, we define a
-pNet template, that can be used as a building node in a hierarchical
-assembly of processes, organised in a tree of sub-groups; communication makes use
-of local broadcast within each sub-group, and uses gateways for
-transmission of messages, up and down, between the subgroups. The
-gateways are described as generic pLTSs, playing the role of
-``controllers'' in the pNet node.
-
-\TODO{start with a simple informal description ?}
-
-More precisely, we model a generic structure supporting
-  hierarchical groups of processes, including gateways. Then
-  we model 3 differents message
-  routing algorithms, plus 2 variants, all working on this same
-  network topology, namely:
-\begin{itemize}
-\item Full broadcast: the message goes up to the root of the
-  tree, then is broadcasted down to all processes in all groups.
-\item Hierarchical broadcast 1: similar to unicast, but within each
-  subgroup the communication uses local broadcast. Only the processes
-  in the same group than the target process will received the
-  message.
-This is the algorithm from the original paper \cite{Taguchi03}, in its
-simplified version without fault tolerance mechanisms.
-\item Hierarchical broadcast 2: same principle, but without horizontal broadcast between sibling processes and gateways: the message has to go up to the enclosing subgroup/gateway, before detecting it can go down to its target.
-\item Unicast: the gateways forward the message using the shortest
-  route in the tree. The message will reach only the specified target.
-\item Unicast 2: same principle, but with detection of sibling situations, and direct sending of messages to sibling gateways/processes, thus shortening the path in a way similar to the Hierarchical Broadcast 1.
-\end{itemize}
-
-We will use these 3 algorithms, and their variants, to illustrate the
-type of properties we can prove using open pNets and FH-bisimulations.
-Note that we cannot hope to get any strong bisimulation equivalences
-between them, the intermediate messages introduced by the protocoles
-are different. To get interesting properties, we must hide
-intermediate messages, and look for weak bisimulation properties.
-
-Here are some examples:
-
-\ERIC{Simple scenario: When hiding everything but send and receive
-  messages from processes, the resulting systems with Unicast and
-  Hierarchical broadcast are weak equivalent
-  ?}
-
-\ERIC{Hierarchical Broadcast Variants: when hiding all horizontal messages
-  the two variants are Weak Equivalent ? (same for Unicast variants) }
-
-\ERIC{What kind of relation with Full broadcast ? This is more tricky,
-on one hand we have to abstract away from the target id in the
-arguments of messages; then full broadcast is indeed broadcasting
-everywhere, so the best we can hope is some refinement relation,
-because Hierachical Broadcast has naturally less behaviours.}
-
-Given a process configuration, organised hierarchicaly in subgroups,
-it is easy to build a pNet tree reflecting the hierarchy, with the
-gateways implementing the 3 algorithms. In the next
-section, we will prove that this model of the implementation is indeed
-equivalent (modulo weak bisimulation) to a flat broadcast.
-
-\medskip
-
-The whole broadcast mechanism of hierarchical groups consists in normal
-processes, gateways and subgroups linked by gateways. Normal processes
-can send and receive messages to/from the other processes (including
-gateways) in the same group, or send up-messages to its enclosing group.
-
-\TODO{Restructure these explanations}
-A gateway has external behaviours : it sends down-messages to its associated
-subgroup, and receives up-messages from its subgroup.
-Gateways behaviour is defined by a simple pLTS with two or three states depending on the algorithm: in the
-initial state the gateway can receive a
-$?m(\widetilde{tgt})$ message (from its neighbors,
-from the enclosing group, or from its own sub-group). Then depending
-on the target address
-$\widetilde{tgt}$, it will forward the message upward as
-$!um(\widetilde{tgt})$, to its corresponding sub-group
-as $!dm(\widetilde{tgt})$, or broadcasted to all its
-neighbors in the same sub-group  as
-$!bm(\widetilde{tgt})$.
-
-\centerline{  \includegraphics[width=\linewidth]{XFIG/SchemaHB+FB}}
-\begin{figure}[h]
-%
-  \caption{Behaviour of a Gateway Broadcast controller }\label{fig:hb-gatewaybroadcast}
-\end{figure}
-
-We will describe the behaviour of the gateways in the next section,
-for the different algorithms and variants.
-
-\paragraph{Sort of the processes.}
-\label{section:processSort}
-The process parameters (the holes of the pNet structure) can emit
-messages with a target address as an argument (we abstract away from
-any other message content), or receive a message, also with the target
-address. But because of the Broadcast mechanism, there are two ways a
-process can send messages, either horizontally, broadcasted to all its
-siblings, denoted $!bm(t)$, or upward to the next hierarchy level,
-denoted $!um(t)$. In the appendix, we
-will propose a way to implement this mechanism using a small pNet as a
-filter. But from now on, this would complexify the examples, so we
-simply assume that the processes have a sort $\{?m(t), !bm(t),
-!um(t)\}$. A process is always ready to accept an incoming message,
-even if the target argument does not match with its own address. The
-filter in the appendix will be in charge of discarding misfit messages.
-
-%\begin{figure}[h]
-% \centerline{  \includegraphics[width=0.7\linewidth]{XFIG/TreeSchema.JPG}}
-%  \caption{Structure of hierarchical groups}\label{fig:tree-schema}
-% \end{figure}
-
-% \TODO{ To use ?m instead of ?bm} => done.
-
-%% \centerline{  \includegraphics[width=0.6\linewidth]{ATG/Gateway}}
-%%   \caption{Bahaviour of a Gateway controller }\label{fig:hb-gateway}
-%%  \end{figure}
-
-%% \paragraph{Variant}
-%% Another try, with a different message name for sub-group broadcast, so
-%% we do not need to pass the src id along... Not sure it makes a simpler
-%% model.
-
-%% \begin{figure}[h]
-
-%% \centerline{  \includegraphics[width=0.8\linewidth]{ATG/Gateway2}}
-%%   \caption{Bahaviour of a Gateway HB controller }\label{fig:hb-gateway2}
-%%  \end{figure}
-%% % \TODO{Eric: to draw the figs of  the broadcast and unicast of
-%% % gateway.} done
-%% \TODO{Min: to give the formal definition of address and predicates}
-
-%% \begin{figure}[h]
-%% \centerline{
-%%   \includegraphics[width=0.5\linewidth]{ATG/GatewayUnicast}
-%%   \hspace{10mm}
-%%   \includegraphics[width=0.4\linewidth]{ATG/GatewayBroadcast}}
-%%   \caption{Bahaviour of Unicast and Broadcast gateways}\label{fig:hb-gatewayunicast}
-%%  \end{figure}
-
-% \centerline{  \includegraphics[width=0.7\linewidth]{XFIG/TreeSchema.JPG}}
-
-According to the three algorithms mentioned above, we have three kinds of pNet models for Unicast, Full broadcast and Hierarchical broadcast.
-
-\begin{definition}[B-pNets]\label{B-pNets}
-A  broadcasting model is a pNet structure : \\
-\centerline{
-$B-\pNet\triangleq \mylangle gw_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}},  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, sg_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}}, \symb{SV}\myrangle $}
-where
-\begin{itemize}
-\item[$\bullet$] $\widetilde{I_G}$ is the index set over which
-  gateways are indexed.  $gw_{\widetilde{g}}^{\widetilde{g}\in
-    \widetilde{I_G}}$ is the family of gateways. $\widetilde{I_G}$ is
-  also the set over which subgroups are indexed,
-  i.e. $gw_{\widetilde{g}}$ links $sg_{\widetilde{g}}$.
-   \begin{itemize}
-   \item Unicast: $\Sort (gw_{\widetilde{g}})=\{?m_{\widetilde{g}}(\widetilde{tgt}), !um_{\widetilde{g}}(\widetilde{tgt}),!dm_{\widetilde{g}}(\widetilde{tgt}), ERROR_{g}\}$
-   \item Flat Broadcast: $\Sort (gw_{\widetilde{g}})=\{?m_{\widetilde{g}}(\widetilde{tgt}), !um_{\widetilde{g}}(\widetilde{tgt}),!dm_{\widetilde{g}}(\widetilde{tgt}), ?um_{\widetilde{g}}(\widetilde{tgt})\}$
-   \item Hierarchical Broadcast: $\Sort (gw_{\widetilde{g}})=\{?m_{\widetilde{g}}(\widetilde{tgt}), ?um_{\widetilde{g}}(\widetilde{tgt}), !um_{\widetilde{g}}(\widetilde{tgt}),!dm_{\widetilde{g}}(\widetilde{tgt}), !bm_{\widetilde{g}}(\widetilde{tgt}),DISCARD,
-       ERROR_{g}\}$
-  \end{itemize}
-\item[$\bullet$] $\widetilde{I_P}$ is the index set over which normal
-  processes are indexed.
-  \item [$\bullet$] $\widetilde{I_{G+P}} \triangleq
-    \widetilde{I_G}\uplus\widetilde{I_P}$ is the index set of all
-    subnets in a group, i.e. processes and subgroups.
-$\widetilde{I_G}$ and $\widetilde{I_P}$ must be \emph{disjoint},
-i.e. $\widetilde{I_G}\cap \widetilde{I_P}=\emptyset$. The sort of
-$pc_{\widetilde{p}}$ is
-\begin{itemize}
-\item Unicast: $\Sort(pc_{\widetilde{p}})=\{!m_{\widetilde{p}}(\widetilde{tgt}),
-?m_{\widetilde{p}}(\widetilde{tgt})\}$
-\item Flat Broadcast: $\Sort(pc_{\widetilde{p}})=\{!m_{\widetilde{p}},
-?m_{\widetilde{p}}\}$
-\item Hierarchical Broadcast: $\Sort(pc_{\widetilde{p}})=\{!um_{\widetilde{p}}(\widetilde{tgt}),
-?m_{\widetilde{p}}(\widetilde{tgt}),
-!bm_{\widetilde{p}}(\widetilde{tgt})\}$
-\end{itemize}
-
-\item[$\bullet$] The subgroup $sg_{\widetilde{g}}$ can be taken the hole of open pNets which can be inserted the sub-pNets(subgroups) and has the sort: $\Sort (sg_{\widetilde{g}})=\{?m_{\widetilde{g}}(\widetilde{t}), !m_{\widetilde{g}}(\widetilde{t})\}$;
-
-\item[$\bullet$]$\symb{SV}$ is a set of synchronisation vectors. For
-  the $HB-\pNet$ node,  we have six kinds of ``normal'' synchronisation
-  vectors in the model, plus 2 ``error'' vectors, listed in
-  Fig. \ref{fig:HBvectors}.
-
-\end{itemize}
-\end{definition}
-
-\centerline{  \includegraphics[width=0.85\linewidth]{ATG/GatewayHB}}
-
-\centerline{
-   \includegraphics[width=0.5\linewidth]{ATG/GatewayUnicast}
-   \hspace{10mm}
-   \includegraphics[width=0.4\linewidth]{ATG/GatewayBroadcast}}
-
-%% \vskip 0.5cm
-%% \begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%% \hline\hline
-%% \multicolumn{3}{|l|}{Full broadcasting}\\
-%% \hline
-%% $(UC)_{\widetilde{k}}$ & $
-%%      \symb{sv}_{u(\widetilde{i}.k)}\triangleq
-%%      <?um_{\widetilde{i}.k}(\widetilde{t})\otimes
-%%      -^{\widetilde{I_P}}\otimes
-%%      !m_{\widetilde{i}.k}(\widetilde{t})\otimes
-%%      -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
-%%          k\}}}>\longrightarrow \tau(
-%%      m_{\widetilde{i}.k}(\widetilde{t}))$ & $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}$\\
-%% \hline
-%% $(DM )_{\widetilde{k}}$& $\symb{sv}_{?\widetilde{i}}\triangleq
-%%      <?m_{\widetilde{i}.k}(\widetilde{t})\otimes
-%%      -^{\widetilde{I_{G+P}}
-%%       \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\otimes -^{\widetilde{I_G}}>\longrightarrow
-%%      ?m_{\widetilde{i}}(\widetilde{t})$&$\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}\uplus \widetilde{I_P}$\\
-%%      \hline
-%% $(UM)_{\widetilde{k}}$&
-%% $\symb{sv}_{!\widetilde{i}}\triangleq
-%%     <!um_{\widetilde{i}.k}(\widetilde{t})\otimes
-%%     -^{\widetilde{I_P}\uplus
-%%       \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\otimes
-%%     -^{\widetilde{I_G}}>\longrightarrow
-%%     !m_{\widetilde{i}.k}(\widetilde{t})$ & $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}\uplus \widetilde{I_P}$\\
-
-%% \hline
-%% $(DG )$&
-%% $\symb{sv}_{?\widetilde{i}}\triangleq
-%%      <?m_{\widetilde{i}.k}^{\forall k\in
-%%        I_K}(\widetilde{t})\otimes
-%%      -^{\widetilde{I_P}}\otimes -^{\widetilde{I_G}}>\longrightarrow
-%%      ?m_{\widetilde{i}}(\widetilde{t})$ & $I_K = \{k/\widetilde{i}.k\in \widetilde{I_G}\uplus
-%% \widetilde{I_P}\}$\\
-
-%% \hline\hline
-%% \end{tabular}
-%% \vskip 0.5cm
-
-%% \begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%% \hline\hline
-%% \multicolumn{3}{|l|}{Unicast broadcasting}\\
-%% \hline
-%% $(UC)_{\widetilde{k}}$ & $
-%%      \symb{sv}_{u(\widetilde{i}.k)}\triangleq
-%%      <?um_{\widetilde{i}.k}(\widetilde{t})\otimes
-%%      -^{\widetilde{I_P}}\otimes
-%%      !m_{\widetilde{i}.k}(\widetilde{t})\otimes
-%%      -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
-%%          k\}}}>\longrightarrow \tau(
-%%      m_{\widetilde{i}.k}(\widetilde{t}))$ & $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}$\\
-%% \hline
-%% $(DM )_{\widetilde{k}}$& $\symb{sv}_{?\widetilde{i}}\triangleq
-%%      <?m_{\widetilde{i}.k}(\widetilde{t})\otimes
-%%      -^{\widetilde{I_P}\uplus
-%%       \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\otimes -^{\widetilde{I_G}}>\longrightarrow
-%%      ?m_{\widetilde{i}}(\widetilde{t})$&$\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}\uplus \widetilde{I_P}$\\
-%%      \hline
-%%      $(UM)_{\widetilde{k}}$&
-%% $\symb{sv}_{!\widetilde{i}}\triangleq
-%%     <!um_{\widetilde{i}.k}(\widetilde{t})\otimes
-%%     -^{\widetilde{I_P}\uplus
-%%       \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\otimes
-%%     -^{\widetilde{I_G}}>\longrightarrow
-%%     !m_{\widetilde{i}.k}(\widetilde{t})$ & $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}\uplus \widetilde{I_P}$\\
-%% \hline
-%% $(DK)_{\widetilde{k}}$&
-%% $\symb{sv}_{!\widetilde{i}}\triangleq
-%%     <!m_{\widetilde{i}.k}(\widetilde{t})\otimes
-%%     ?m_{\widetilde{i}.g}(\widetilde{t})\otimes -^{\widetilde{I_P}\uplus
-%%       \widetilde{I_G}\backslash\{\widetilde{i}\cdot k,\widetilde{i}\cdot g\}}\otimes
-%%     -^{\widetilde{I_G}}>\longrightarrow
-%%     \tau(m_{\widetilde{i}.k}(\widetilde{t}))$ & $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}\uplus \widetilde{I_P}$\\
-
-%% \hline\hline
-%% \end{tabular}
-%\end{definition}
-
-%
-%  \begin{itemize}
-%  \item[$(BG)_{\widetilde{k}}$]
-%    $\symb{sv}_{b(\widetilde{i}.k)}\triangleq
-%    <?m_{\widetilde{i}.j}^{\forall j\in I_K}(\widetilde{t})
-%    \otimes !bm_{\widetilde{i}.k}(\widetilde{t})
-%    \otimes -^{\widetilde{I_G}}>\longrightarrow \tau( bm(\widetilde{t}))$,
-%where $I_K = \{k/\widetilde{i}.k\in \widetilde{I_G}\uplus
-%\widetilde{I_P}\}$, and $\widetilde{k}=\widetilde{i}.k$
-%
-%  \item [$(UM)_{\widetilde{k}}$] $
-%    \symb{sv}_{!\widetilde{i}}\triangleq
-%    <!um_{\widetilde{i}.k}(\widetilde{t})\otimes
-%    -^{\widetilde{I_P}\uplus
-%      \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\otimes
-%    -^{\widetilde{I_G}}>\longrightarrow
-%    !m_{\widetilde{i}.k}(\widetilde{t})$,
-%where $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}\uplus \widetilde{I_P}$;
-%
-%   \item [$(DC)_{\widetilde{k}}$] $
-%     \symb{sv}_{d(\widetilde{i}.k)}\triangleq
-%     <!dm_{\widetilde{i}.k}(\widetilde{t})\otimes
-%     -^{\widetilde{I_P}}\otimes
-%     ?m_{\widetilde{i}.k}(\widetilde{t})\otimes
-%     -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}}
-%     >\longrightarrow
-%     \tau(m_{\widetilde{i}.k}(\widetilde{t}))$,
-%where $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}$;
-%
-%   \item [$(UC)_{\widetilde{k}}$] $
-%     \symb{sv}_{u(\widetilde{i}.k)}\triangleq
-%     <?um_{\widetilde{i}.k}(\widetilde{t})\otimes
-%     -^{\widetilde{I_P}}\otimes
-%     !m_{\widetilde{i}.k}(\widetilde{t})\otimes
-%     -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
-%         k\}}}>\longrightarrow \tau(
-%     m_{\widetilde{i}.k}(\widetilde{t}))$,
-%where $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}$;
-%
-%   \item [$(DG )$] $\symb{sv}_{?\widetilde{i}}\triangleq
-%     <?m_{\widetilde{i}.k}^{\forall k\in
-%       I_K}(\widetilde{t})\otimes
-%     -^{\widetilde{I_P}}\otimes -^{\widetilde{I_G}}>\longrightarrow
-%     ?m_{\widetilde{i}}(\widetilde{t})$,
-%where $I_K = \{k/\widetilde{i}.k\in \widetilde{I_G}\uplus
-%\widetilde{I_P}\}$.
-%
-% \item [$(DM )_{\widetilde{k}}$] $\symb{sv}_{?\widetilde{i}}\triangleq
-%     <?m_{\widetilde{i}.k}(\widetilde{t})\otimes
-%     -^{\widetilde{I_P}\uplus
-%      \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\otimes -^{\widetilde{I_G}}>\longrightarrow
-%     ?m_{\widetilde{i}}(\widetilde{t})$,
-%where $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}\uplus \widetilde{I_P}$;
-%
-%\item [$(DIS)_{\widetilde{k}}$] $\symb{sv}_{dc}\triangleq
-%     <DISCARD_{\widetilde{i}.k}^{\forall k\in
-%       I_K}(\widetilde{t})\otimes
-%     -^{\widetilde{I_P}}\otimes -^{\widetilde{I_G}}>\longrightarrow
-%     \tau(m_{\widetilde{i}.k}(\widetilde{t}))$,
-%where $I_K = \{k/\widetilde{i}.k\in \widetilde{I_G}\uplus
-%\widetilde{I_P}\}$.
-%\end{itemize}
-%\end{itemize}
-
-\medskip
-
-   \begin{example}
-We sketch here one example showing how to send one message from one
-process in one group to the other process in the other group by using
-broadcast mechanism of Hierarchical groups in {\sl HB-pNets}. Here we
-use 12, 122,... instead of the denotation above 1.2 , 1.2.2,... in the
-definition for short.
-   \end{example}
-
-\begin{figure}[h]
-  \includegraphics[width=1.0\linewidth]{ATG/Inst5}
-  \caption{A Hierarchical Broadcast pNet Structure }\label{fig:hb-structure}
- \end{figure}
-
-In Fig.~\ref{fig:hb-structure}, suppose that one root group $G$ has
-  two gateways $g_1$ and $g_2$ which link two subgroups $G_1$ and
-  $G_2$, and a normal process $P_3$. Subgroup $G_1$ has one gateway $g_{12}$ which links the
-  subsubgroup $G_{12}$ one normal process $P_{12}$.
-  $G_2$ and $G_{11}$ have two normal processes respectively.
-
-The procedure of sending one message from process $P_{21}$ to process
-$P_{122}$ can be described as follows:
-
-\TODO{To be written, unless it is already in a previous section ?}
-
-\section{Computing the open operational semantics}
-
-In this section we show how to unfold the operational semantic rules
-on our hierarchical broadcast example, compute open transitions, and
-start building the open automaton.
-
-The sketch we give here considers one particular pNet node, with 2
-subgroups, and a specific number of processes in each root- and sub-
-groups. Also we make some hypotheses on the sorts of the processes.
-Clearly the full proof will have to deal with generalisations of this
-particular case.
-
-% \newcommand{\NetS}[1]{\symb{\guillemotleft} #1 \symb{\guillemotright}}
-
-%% A transition in the proof tree is either :
-%% \begin{itemize}
-%% \item a transition in a pLTS, with eventually a state change.
-%% \item an action in the sort of a Hole.
-%% \item the ``global action'' resulting from a synchronisation vector in the pNet.
-%% \end{itemize}
-
-%% \begin{figure}[h]
-%% $\NetS{0_{g1}, 0_{g2}, \sm{P3}, \NetS{0_{g11}, \sm{P12}, \sm{P13},
-%%       \sm{SG11}}, \NetS{\sm{P21}, \sm{P22}}}$
-%% \hfill
-%% $<<0_{g1}, 0_{g2}, 0_{g11}>>$
-
-%% \caption{initial state of our example, and state of the corresponding Expr}
-%% \end{figure}
-
-For each possible synch vector of the root node, we build a proof
-tree. From each such proof tree we derive a {\em open transition},
-representing a symbolic transition in the open automaton
-of the pNet.
-%% Now we compute the corresponding open-transition, getting rid of the
-%% intermediate deduction steps, keeping only premisses for the pLTS
-%% and holes involved, and the predicate.
-
-%% \begin{mathpar}
-%%   \inferrule
-%%       {0_{gw2} \xrightarrow{a_{gw2}} 2_{gw2} \\
-%%            \xrightarrow{b_{P21}}
-%%            \\ Pred_{Root}
-%%       }
-%%            {\ostate{000} \xrightarrow{v} \ostate{020}}
-%%       ~~ [UG\_2(UM\_21)]
-%% \end{mathpar}
-
-\medskip
-Following the residual algorithm from section \ref{sec:xxx}, we can
-build the full open-automaton of our pNet. We give here in Figure
-\ref{fig:xxx} only a small view of its first two states.
-
-\paragraph{Proving equivalences}
-
-We present a (partial) set of transitions of our two processes in the
-following tables. For each state of the expression, we have a set of
-lines, each defining one open transition starting from this state.
-For each specific+ation rule, we show the vectors used to prove it, the
-formal hypothesis and the predicte, and the resulting expression
-state.
-
-The resulting LTS for our example is shown in Fig. \ref{fig:HB-lts}.
-
-\begin{figure}[h]
-\includegraphics[width=9cm]{ATG/FullLTS}
-
-\caption{(symbolic) behaviour of the example, Hierarchical version}
-\label{fig:HB-lts}
-\end{figure}
-
-For the flattened version, the computation of the symbolic graph is similar, but of course simpler. The result is shown in Fig. \ref{fig:Flat-lts}.
-
-\begin{figure}[h]
-\includegraphics[width=9cm]{ATG/FlatLTS}
-
-\caption{(symbolic) behaviour of the example, Flat version}
-\label{fig:Flat-lts}
-\end{figure}
-
-%%% REVISION: what we did:
-%%% added the notation (x|-> J) page 3 (used to define composition)
-%%% defined pnet composiiton (filling a hole)
-%%% defined pnests bisimilarity (trivial)
-%%% added constraint on synchronisation vector: no fresh variable in target action
-%%% changed Pred def: iff instead of implies

### 2017-02-08 2016-Weak-FH-Bisim/WeakBisim.tex
\cite{Forte2016}
Proof of transitivity for FH bisim

@@
 FH-bisimulation provided the logic of the predicates is decidable (see
-\cite{Forte2016}). }
+\cite{henrio:Forte2016}). }
 
@@
 values of $s^2$ are collected by a disjunction.
- we will show
-that $\mathcal{R}''$ is an FH-bisimulation. Let
-$(s^1,s^2|\Pred)\in\mathcal{R}$,  we have the followings since
-
-\TODO{LUDO: I stopped rewriting here}
-For any open transition $OT$ in $\mathcal{T}_1$:
-
+
+ We will show
+that $\mathcal{R}''$ is an FH-bisimulation. Consider 
+$(s^1,s^3|\Pred\,'')\in\mathcal{R}''$. Then there is a set of states of 
+$\mathcal{T}_2$ relating $s^1$ and $s^3$, let $(s^2_p)^{p\in P}$ be this family.
+
+For any $p\in P$ by definition of $\mathcal{R}''$,
+$(s^1,s^2_p|\Pred_p)\in\mathcal{R}$,  and $(s^2_p,s^3|\Pred\,'_p)\in\mathcal{R}$. We have 
+the 
+following by definition of bisimulation.
+For any open transition $OT$ in $\mathcal{T}_1$ originating from $s^1$:
+Additionally we have $\Pred\,'' = \bigvee_{p\in P} \Pred_p\land\Pred_p\,'$.
 \begin{mathpar}
@@
 \inferrule*[myfraction=\reddottedrule]
-{\{s^1_i\xrightarrow{a_i}_i s^{1'}_i\}^{i\in I_1}, % , s^1_i,s^{1'}_i\in
+{\{s^1_i\xrightarrow{a_i}_i {s^{1}}'_i\}^{i\in I_1}, % , s^1_i,s^{1'}_i\in
 	%States(I_1)
 	\{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
-{s^1 \xrightarrow {v} s^{1'}}
+{s^1 \xrightarrow {v} {s^{1}}'}
 
@@
 
-there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
+there exist open transitions $OT_{p x}^{x\in X} \subseteq \mathcal{T}_2$:
 
@@
 \inferrule*[myfraction=\reddottedrule]
-{\{s^{2}_i\xrightarrow{a_{i x}}_i s^{2}_{i x}\}^{i\in I_{2 x}},
-	\{\xrightarrow{b_{j x}}_j\}^{j\in J_{2x}}, \Pred_{OT_x},\Post_{OT_x}}
-{s^2 \xrightarrow {v_x} s^{2}_x}
+{\{s^{2}_{pi}\xrightarrow{a_{p i x}}_i s^{2}_{p i x}\}^{i\in I_{2 p x}},
+	\{\xrightarrow{b_{j p x}}_j\}^{j\in J_{2px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
+{s^2_p \xrightarrow {v_{px}} s^{2}_{px}}
 %         \right)
@@
 
-such that  $\forall x, J_1=J_{2x}, (s^{1'},s^{2}_x|\Pred_{target_x})\in 
+such that  $\forall x, J_1=J_{2px}, (s^{1'},s^{2}_{px}|\Pred_{target_{px}})\in 
 \mathcal{R}$;
@@
 
-$\Pred \land \Pred_{OT}\\
+$\Pred_p \land \Pred_{OT}\\
 \hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-\left( \forall j. b_j=b_{jx}  \Rightarrow \Pred_{OT_x}
-\land v\!=\!v_x \land
-\Pred_{target_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
-
-for any open transition $OT_x$, since
-$(s^2,s^3|\Pred^\prime)\in\mathcal{R}$ there exist open transitions
-$OT_{xy}^{x\in X, y\in Y} \subseteq \mathcal{T}_3$:
+\left( \forall j. b_j=b_{jpx}  \Rightarrow \Pred_{OT_{px}}
+\land v\!=\!v_{px} \land
+\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)$
+
+for any open transition $OT_{px}$, since
+$(s^2_p,s^3|\Pred\,^\prime_p)\in\mathcal{R}'$ there exist open transitions
+$OT_{pxy}^{x\in X, y\in Y} \subseteq \mathcal{T}_3$:
 
@@
 \inferrule*[myfraction=\reddottedrule]
-{\{s^{3}_i\xrightarrow{a_{i x y}}_i s^{3}_{i xy}\}^{i\in I_{3 xy}},
-	\{\xrightarrow{b_{j x y}}_j\}^{j\in J_{3xy}}, \Pred_{OT_{xy}},\Post_{OT_{xy}}}
-{s^3 \xrightarrow {v_{xy}} s^{3}_{xy}}
+{\{s^{3}_i\xrightarrow{a_{i p x y}}_i s^{3}_{i p x y}\}^{i\in I_{3 p x y}},
+	\{\xrightarrow{b_{j p x y}}_j\}^{j\in J_{3pxy}}, \Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
+{s^3 \xrightarrow {v_{pxy}} s^{3}_{pxy}}
 %         \right)
@@
 \end{mathpar}
-\TODO{LUDO: I have trouble doing computing the next line without intermediates: it is an 
-iterative application of many FH bisim definitions with reordering of terms and 
-manipulation of quantifiers}
-such that  $\forall x, \forall y, J_1=J_{2x}=J_{3xy}, 
-(s^{1'},s^{3}_{xy}|\Pred_{target_{xy}})\in \mathcal{R}$; and  \\
-$\Pred\,' \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}
-\left( \forall j. b_j=b_{jx}=b_{jxy}  \Rightarrow \Pred_{OT_{xy}}
-\land v\!=\!v_{xy} \land
-\Pred_{target_{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{xy}}}\right)$.
-
-\TODO{the proof is incomplete because it does not deal with predicates and does not 
-explicit what is the right $pred''$ $\implies$ TODO}
+such that  $\forall y, J_{2px}=J_{3pxy}, 
+(s^{2}_x,s^{3}_{pxy}|\Pred_{target_{pxy}})\in \mathcal{R}'$; and  \\
+$\Pred\,'_p \land \Pred_{OT_x}\\
+\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
+\left( \forall j. b_{jpx}=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
+\land v_{px}\!=\!v_{pxy} \land
+\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.
+
+This is verified for each $p\in P$. Overall,  we have a family of open transitions 
+$OT_{pxy}^{p\in 
+P, x\in X, 
+y\in Y} \subseteq \mathcal{T}_3$ that should simulate \emph{OT}.
+
+First, $\forall y, \forall x, \forall p, J_1=J_{2px}=J_{3pxy}, 
+({s^{1}}',s^{3}_{pxy}|\Pred\,'_{target_{pxy}})\in \mathcal{R}''$. 
+Indeed for any 
+$p$, 
+$x$, and 
+$y$, $s^2_{px}$
+relate ${s^{1}}'$ and $s^{3}_{pxy}$, indeed
+$(s^{1'},s^{2}_{px}|\Pred_{target_{px}})\in \mathcal{R}$
+ and $(s^{2}_x,s^{3}_{pxy}|\Pred_{target_{pxy}})\in \mathcal{R}'$. 
+ More precisely, $s^{2}_{px} \in ({s^{2}_p}')^{p\in P'}$ where $({s^{2}_p}')^{p\in 
+ P'}$ 
+ is 
+ the set of states relating ${s^{1}}'$ and $s^{3}_{pxy}$.
+Consequently, for all $p$, $x$, $y$, $\Pred_{target_{px}}\land 
+\Pred_{target_{pxy}}\implies 
+\Pred\,'_{target_{pxy}}$ (this is one element of the  disjunction defining the 
+predicate 
+relating ${s^{1}}'$ and $s^{3}_{pxy}$ in the definition of $\mathcal{R}''$).
+
+Second, we need \\
+\begin{small}
+$\Pred\,'' \land \Pred_{OT}\\
+\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
+\left( \forall j. b_j=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
+\land v\!=\!v_{pxy} \land
+\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
+\end{small}
+
+We have, for all $p$
+\begin{small}
+$\Pred_p \land \Pred_{OT}\land\Pred'_p\\
+\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
+\left( \forall j. b_j=b_{jpx}  \Rightarrow \Pred_{OT_{px}}
+\land v\!=\!v_{px} \land
+\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\land\Pred'_p\\
+%
+\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
+\left( \forall j. b_j=b_{jpx}  \Rightarrow (\Pred_{OT_{px}}\land\Pred'_p)
+\land v\!=\!v_{px} \land
+\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\\
+%
+\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
+\big( \forall j. b_j=b_{jpx}  \Rightarrow (\bigvee_{y\in Y} 
+\big( \forall j'. b_{j'px}=b_{j'pxy}  \Rightarrow \Pred_{OT_{pxy}}
+\land v_{px}\!=\!v_{pxy}\\\hspace{3em}~ \land
+\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\big))
+\land v\!=\!v_{px} \land
+\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\\
+%
+\hspace{1cm} \implies\!\!\! \bigvee_{x\in X} \bigvee_{y\in Y}
+\big( \forall j, j'. b_j=b_{jpx} \land b_{j'px}=b_{j'pxy}
+\Rightarrow \big( 
+\Pred_{OT_{pxy}}
+\land v\!=v_{px}\!=\!v_{pxy}\\\hspace{3em}~ \land
+\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}
+ \land
+\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\big)
+$
+
+\end{small}
+
+Additionally, the Post renamings do not modify the predicates that only use non-renamed 
+variables, and because of the domain of the renamings:\\
+$\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\land 
+\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
+= 
+\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land 
+\Pred_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
+\implies\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
+= \Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}} $
+
+This allows us to conclude: using $\Pred\,'' = \bigvee_{p\in P} \Pred_p\land\Pred_p\,'$ 
+and the assertions above we obtained the needed property.
+
+\smallskip
+Concerning the other direction of bisimulation, it is sufficient to notice that the role 
+of $s^1$ and $s^3$ in the definition of $\mathcal{R}''$ is symmetrical, and thus the 
+proof is similar.
 

### 2017-02-09 2017-Xudong-SMT/pNetZ3paper.tex
Push testing - Generating algorithm
The description of OA generating algorithm.

--- 2017-02-02 2017-Xudong-SMT/OpenPNets-SMT.tex
@@
-% !TEX TS-program = pdflatex
-
 \documentclass{lncs/llncs}
@@
 
-\title{Using SMT engine to generate Symbolic Automata\thanks{This work was partially 
-funded by the Associated Team FM4CPS
-  between INRIA and ECNU, Shanghai}}
-\author{ Xudong Qin\inst{3}  \ \ \  Eric Madelaine\inst{1,2}} 
-\institute{Univ. of Nice Sophia Antipolis, CNRS, UMR 7271, 06900 Sophia Antipolis, France
-	\and INRIA Sophia Antipolis M\'edit\'erann\'ee, BP 93, 06902 Sophia Antipolis, France
-\and Shanghai Key Laboratory of Trustworthy Computing, ECNU, China}
-\date{}                                           % Activate to display a given date or no date
-
-                          % Activate to display a given date or no date
-
 \begin{document}
 
-\maketitle
+\begin{algorithm}[Operational Semantics Generation Algorithm of Open pNets]
+Open transitions satisfying two rules:
+The rule for pLTSs (Tr1) and the rule deal with pNet nodes (Tr2).
+Tr2 uses Tr1 and Tr2 recursively if there are subnets of the pNet.
+So the structure of the open transitions and subnets' open transitions is like a deduction tree constructively "prove" the open transition.
+To generate the list of possible open transitions for the pNet, we build all the possible deduction trees from the given start global state according to these two rules.
 
-%\section{}
-%\subsection{}
+\begin{description}
+\item[{Tr1 :}]
+\end{description}
 
-\begin{abstract}
-  We implement the symbolic semantics of open pNets using their
-  so-called ``Open Automaton'' behavioural semantics. This involve
-  building predicates expressing the synchronisation conditions
-  allowing some combination of events in the pNet system. These
-  predicates are typically built using first order logic, plus some
-  predicates specific of particular action algebras. To reduce the
-  complexity of the generated open automata, we use the Z3 SMT engine
-  to check satisfiability of the predicates, and prune the state
-  space..
+1) Get the start state of the pLTS.
 
-\end{abstract}
+2) For all the transitions start with the start state.
 
-\section{Introduction}
+       2a) Get the target state of the transition. Generate the target global state according to the target state.
 
-\ERIC{imported from FORTE'16, }
+       2b) Get the guard of the transition, add it into the predicate of the open transition.
 
-In the nineties, several 
-works extended the basic behavioural models based on labelled
-transition systems to address value-passing or parameterised systems, using
-various symbolic encodings of the
-transitions~\cite{deSimone85,Larsen87,HennessyLin:TCS95,Linconcur96}. 
-In \cite{Linconcur96}, H.M. Lin addressed value-passing calculi, for which he
-developed a symbolic behavioural semantics, and proved algebraic properties.
-Separately J. Rathke~\cite{HennessyRathke:TCS98} defined another
-symbolic semantics for 
-a parameterised broadcast calculus, together with strong and weak bisimulation
-equivalences, and developed a symbolic model-checker based on a tableau
-method for these processes. 30 years later, no
-practical verification approach and no verification platform are
-using this kind of approaches to provide proof methods for
-value-passing processes or open process expressions.
+       2c) Store the generated open transition in the open transition list.
 
-\paragraph{Context}
-\TODO{
-  Summary of previous works on pNets and open pNets => 1/2 page.\\
-  Longterm goals:\\
-  - open pNets to represent operators and program skeletons (ref to
-  \cite{PDP2015})\\
-  - compute semantics in term of open transitions\\
-  - compute equivalence (bisimulation of open automata)\\
-  - model-check properties of open systems
-  }
-\paragraph{Contribution}
+\begin{description}
+\item[{Tr2 :}]
+\end{description}
 
-\paragraph{Related works}
+It is more complicated, the synchronization vector need to be cloned, the variable actions need a fresh variable, and it need deal with the parameters come from the subnet.
 
-\paragraph{Structure.}
+1) Initialize three counters for the subnet, hole behavior, result action and SV.
 
-\section{Running Example(s)}
+2) Judge the type of all the subnets of the pNet.
+	\begin{itemize}
 
-\section{Parameterised Networks (pNets): definition}
-\label{section:pnets}
+        \item If it is a pLTS, use the Tr1 recursively, store the open transitions list of the pLTS in the list of keeping subnets' open transitions.
 
-\ERIC{Keep minimum defs here too be independent from FORTE}
+        \item If it is a hole, generate a new hole behavior for the open transition. 
+           2a) Count the number. The hole behavior counter increases one.
 
-This section introduces pNets and the notations we will use in
-this paper. Then it gives the formal definition of pNet structures,
-together with an operational semantics for open pNets.
+           2b) Build a fresh hole behavior.
 
-pNets are tree-like structures, where the leaves are either
-\emph{parameterised labelled transition systems (pLTSs)}, expressing the
-behaviour of basic processes, or \emph{holes}, used as placeholders
-for unknown processes, of which we only specify the set of possible
-actions, this set is named the \emph{sort}.
-Nodes of the tree (pNet nodes) are synchronising artifacts, using a
-set of \emph{synchronisation vectors} that express the possible
-synchronisation between the parameterised actions of a subset of the
-sub-trees.
+           2c) Generate the hole behavior. Store it in the hole behaviors list of the open transition.
 
-%\smallskip\noindent
-\paragraph*{Notations.}
-We extensively use indexed structures
-over some countable indexed sets, which are equivalent to mappings over
-the countable set. % . The indexes will usually be
-% integers, bounded or not. Such an indexed family is
-%denoted
-%follows:
-$a_i^{i\in I}$
-%, or equivalently  $(i\mapsto a_i)^{i\in I}$
-denotes a family of elements $a_i$ indexed over the
-set $I$. % Such a family
-% is equivalent to the mapping $(i\mapsto a_i)^{i\in I}$.
-% To specify the set over which the structure is indexed,
-% indexed structures are always denoted with an exponent of the form $i\in I$
-% (arithmetic only appears in the indexes if necessary).
-$a_i^{i\in I}$ defines both $I$ the set over which the family is
-indexed (called \emph{range}), and $a_i$ the elements of the family.
-E.g., $a^{i\in\{3\}}$ is the mapping with a single entry $a$ at index
-$3$ ; abbreviated $(3\mapsto a)$ in the following.
-When this is not
-ambiguous, we shall use notations for sets, and typically write
-``indexed set over I'' when formally we should speak of multisets, and
-write $x\in a_i^{i\in I}$ to mean $\exists i\in I.\, x=a_i$.  An empty
-family is denoted $\emptyset$. We
-denote classically $\overline{a}$ a family when the indexing set is
-not meaningful.  $\uplus$ is the disjoint union on
-indexed sets.
-
-\paragraph*{Term algebra.}
-Our models rely on a notion of parameterised actions, that are
-symbolic expressions using data types and variables. As our model aims
-at encoding the low-level behaviour of possibly very different
-programming languages, we do not want to impose one specific algebra
-for denoting actions, nor any specific communication mechanism. So we
-leave unspecified the constructors of the algebra that will allow building
-expressions and actions. Moreover, we use a generic {\em action interaction}
-mechanism, based on (some sort of) unification between two or more action
-expressions, to express various kinds of communication or
-synchronisation mechanisms.
-
-\def\Talg{\mathcal{T}_{\Sigma,\P}}
-Formally, we assume the existence of a term algebra $\Talg$,
-where $\Sigma$ is the signature of the data and action constructors,
-and $\P$ a set of variables. Within $\Talg$, we distinguish a set of
-data expressions $\mathcal{E}_\P$, including a set of boolean
-expressions $\mathcal{B}_{\P}$ ($\mathcal{B}_{\P}\subseteq\mathcal{E}_\P$).
-On top of $\mathcal{E}_\P$ we build the action algebra
-$\mathcal{A}_\P$, with $\mathcal{A}_P\subseteq\mathcal{T}_\P,
-\mathcal{E}_P\cap\mathcal{A}_P=\emptyset$;
-naturally action terms will use data expressions as subterms.
-To be able to reason about the data flow between pLTSs, we
-distinguish \emph{input variables} of the form $?x$ within terms; the function
-$\vars(t)$ identifies the set of variables in a term
-$t\in\AlgT$, and $iv(t)$ returns its input variables.
-
-pNets can encode naturally the notion of input actions in value-passing CCS
-\cite{Milner89} or of usual point-to-point message passing calculi, but it also allows
-for more general mechanisms, like gate negociation in Lotos, or broadcast
-communications. Using our notations, value-passing actions \emph{\`a la} CCS would be
-encoded as $a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs (in which $v_i$ are 
-action terms containing no input variables). 
-%For Lotos-style
-%distributed synchronisation, we use synchronisation vectors that encode matching data
-%offers on a common gate; or 
-We can also use more complex action structure such as Meije-SCCS action
-monoids, like in $a.b$, $a^{f(n)}$ (see \cite{deSimone85}). The expressiveness of the synchronisation constructs
-will depend on the action algebra.
-
-\subsection{The (open) pNets Core Model}
-\label{section:pNets}
-
-A pLTS is a labelled transition system with variables; variables can be
-manipulated, defined, or accessed inside states, actions, guards, and
-assignments. Without loss of generality and to simplify the formalisation, we suppose 
-here that 
-variables are local to each 
-state: each state has its set of variables disjoint from the others. Transmitting 
-variable values from one state to the other can be done by explicit assignment. 
-%Similarly, to simplify the management of variables and without loss of expressivity, we 
-%suppose that transitions looping to the same state does not do assignments.
-Note that we make no assumption on finiteness of the set of states nor
-on finite branching of the transition relation.
-
-We first define the set of actions a pLTS can use, let $a$
-range over action labels, $\symb{op}$ are operators, and $x_i$ range over
-variable names. Action terms are:
-\[
-\begin{array}[l]{rcl@{\quad}p{5.5cm}}
-  \alpha\in\AlgA&::=&a(p_1,\ldots,p_n)&\text{action terms}\\
-  p_i&::=& ?x~|~\symb{Expr}&\text{parameters (input variable or expression)}\\
-  \symb{Expr}&::=& \symb{Value}~|~x~|~\symb{op}(\symb{Expr}_1,..,\symb{Expr}_n)&\text{Expressions}
-\end{array}
-\]
-The input variables in an action term are those marked with a
-$\symb{?}$.
-We additionally suppose that each input variable does not
-appear somewhere else in the same action term:
-$p_i=?x\Rightarrow\forall j\neq i.\, x\notin \vars(p_j)$
-
-\begin{definition}[pLTS]
-\label{pLTS}
-A pLTS is a tuple
-$pLTS\triangleq\mylangle S,s_0, \to\myrangle$ where:
-\begin{itemize}
-\item[$\bullet$]
-$S$ is a set of states.
-\item[$\bullet$]
-$s_0 \in S$ is the initial state.
-%\item[$\bullet$]
- %Variables in
-%$\iv(\alpha)$ are assigned by the action, other variables can be assigned
-%by the additional assignments.
-\item[$\bullet$] $\to \subseteq S \times L \times S$ is the transition relation and 
-$L$ is the set of labels of the form
-$\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in J}\rangle$,
-where $\alpha \in\AlgA$ is a parameterised action, $e_b \in
-\AlgB$ is a guard, and the variables $x_j\in P$
-are assigned the expressions $e_j\in \AlgE$.
-If 
-$s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
-		J}\rangle} s'\in \to $ then $\iv(\alpha)\!\subseteq\! \vars(s')$, 
-		$\vars(\alpha)\backslash \iv(\alpha)\!\subseteq\! \vars(s)$, 
-		$\vars(e_b)\!\subseteq\! \vars(s')$, and
-		$\forall j\!\in\! J .\,\vars(e_j)\!\subseteq\! \vars(s)\land 
-		x_j\!\in\!\vars(s')$. %,  and $s= s'\Rightarrow J=\emptyset$.
+        \item If it is a pNet, use the Tr2 recursively, store the open transitions list of the subnet in the list of keeping subnets' open transitions.
 
 	\end{itemize}
-\end{definition}
 
-Now we define
-pNet nodes, as constructors for hierarchical behavioural structures.
-A pNet has a set of sub-pNets that can be either pNets or pLTSs, and a
-set of Holes, playing the role of process parameters.
+ 3) Generate a new result action for the open transition.
 
-A composite pNet consists of a set of sub-pNets exposing
-a set of actions, each of them triggering internal actions in each of
-the sub-pNets. The synchronisation between global actions and
-internal actions is given by  \emph{synchronisation vectors}: a
-synchronisation vector synchronises one or several internal actions, and
-exposes a single resulting global action.
-Actions involved at the pNet level (in the synchronisation vectors) do
-not need to distinguish between input and output
-variables. Action terms for pNets are defined as follows:
-\[\begin{array}[l]{rcl@{\quad}l}
-  \alpha\in \AlgAS &::=&a(Expr_1,\ldots,Expr_n)
-\end{array}
-\]
+       3a) Count the number. The result action counter increases one.
 
-\begin{definition}[pNets]\label{def-pnets}
-A pNet is a hierarchical structure where leaves are pLTSs and holes:\\
-$\pNet\triangleq pLTS~|~\mylangle \pNet_i^{i\in I}, S_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle$
-where
+       3b) Build a fresh result action.
+
+ 4) For all SVs of the pNet.
+
+       4a) Match result action and the combination of the subnets' open transitions and hole behaviors with the SV to generate the predicates of the open transition.
+Then a possible open transition of the pNet is generated.
+Every time the SV is chosen it need be cloned and the cloned one is used for matching.
+Similarly, the variable elements of the combination are also need fresh variables.
+
+       4b) Store the open transition of the pNet in the open transition list.
+
+\end{algorithm}
+
+In addition, the format of fresh variable (renaming) is already defined as
+$$\emph{prefix : tree\ index:counter}$$
 \begin{itemize}
-\item[$\bullet$] $I \in \I$ is the set over which sub-pNets are indexed.
-\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets.
-%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which sub-pNets are indexed.
-
-\item[$\bullet$] $J\in\I_\P$ is the set over which holes are indexed.
-$I$ and $J$ are \emph{disjoint}: $I\cap J=\emptyset$,  $I\cup J\neq\emptyset$
-\item[$\bullet$] $S_j \subseteq \AlgAS$ is a set of action terms, denoting the $\Sort$ of
-hole $j$.
-
-\item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
-  synchronisation vectors ($K\in\I_\P$). $\forall k\!\in\! K,
-  \symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k$ where
-  $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
-  $\forall i\!\in\!
-  I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$,  $\forall j\!\in\!
-  J_k.\,\alpha_{j}\!\in\!S_j$, and $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
-  J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
-$\Label(\symb{SV}_k) = \alpha'_k$.
-
-\end{itemize}
-\end{definition}
-
-The preceding definition relies on the auxiliary functions below:
-
-\begin{definition}[Sorts, Holes, Leaves of pNets]
-  \begin{itemize}
-  \item The sort of a pNet is its signature, i.e. the set of actions it can
-perform. In the definition of sorts, we do not need to distinguish
-input variables (that specify the dataflow within LTSs), so for
-computing LTS sorts, we use a substitution operator\footnote{$\subst{y_k\gets x_k}^{k\in K}$ is the parallel substitution 
-operation.} to remove the
-\emph{input marker} of variables. Formally:
-\[
-\begin{array}{l}
-\Sort(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{x \gets ?x| 
-x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
-		J}\rangle} s'\in \to \} \\ \Sort(\mylangle
-\set{\pNet}, \set{\symb{S}}, \set{\symb{SV}}\myrangle) =\{\alpha'_k |\, \alpha_j^{j\in J_k}\to\alpha'_k\in\set{\symb{SV}}\}
-\end{array}
-\]
-
-\item
-The set of holes of a pNet is defined inductively; the sets of holes
-in a pNet node and its subnets are all disjoint:
-  \[\begin{array}{l}
-\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset \\
-\Holes(\mylangle \pNet_i^{i\in I}\!,S_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) =J\cup{\displaystyle \bigcup_{i\in I}\Holes(\pNet_i)}\\
-\forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
-\forall i_1,i_2\in I.\,i_1\neq i_2\Rightarrow  \Holes(\pNet_{i_1})\cap\Holes(\pNet_{i_2})=\emptyset
-\end{array}\]
-\item
-The set of leaves of a pNet is the set of all pLTSs occurring in the structure, defined inductively as:
-\[\begin{array}{l}
-\Leaves(\mylangle S,s_0, \to\myrangle) \!=\! \{ \mylangle S,s_0, \to\myrangle \}\\
-\Leaves(\mylangle \pNet_i^{i\in I}\!,S_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \bigcup_{i\in I}\Leaves(\pNet_i)}
-\end{array}\]
-\end{itemize}
-\end{definition}
-
-A pNet $Q$ is \emph{closed} if it has no hole: $\Holes(Q)=\emptyset$; else it
-is said to be \emph{open}.
-
-\begin{figure}[t]
-\begin{minipage}{6.1cm}
-
-  \includegraphics[width=\linewidth]{XFIG/Enable1}
-  \\[1.3ex]
- \includegraphics[width=\linewidth]{XFIG/Enable2}
-  \caption{Two pNet encodings for  Enable }  \label{schema:enable-pnets}
-\end{minipage}
-  \hspace{2mm}
-\begin{minipage}{6cm}
-  \includegraphics[width=\linewidth]{XFIG/P-QR}
-  \caption{Composed pNet for ``P>>(Q>>R)''}  \label{schema:enable-composed}
-\end{minipage}
-
-\end{figure}
-
-\section{Operational Semantics for Open pNets}
-\label{section:op-semantics}
-
-The semantics of open pNets will be defined  as an open automaton. An open
-automaton is an automaton where each transition composes transitions of several LTSs with
-action of some holes, the transition occurs if some predicates hold, and can involve a 
-set of state modifications.
-
-\begin{definition}[Open transitions]
-	\label{def:OpenTransitions}
-	An \emph{open transition} over a set  $(S_i,s_{0 i}, \rightarrow_i)^{i\in
-	I}$ of LTSs, a
-	set $J$ of holes with sorts $Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is a structure of the form:	
-	\begin{mathpar}
-	\inferrule*[myfraction=\reddottedrule]
-	{\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
-		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred, \Post}
-	{s \xrightarrow {v}s'}
-	\end{mathpar}
-	Where $s, s'\in\mathcal{S}$ and for all
-        $i\in I$, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the
-	LTS $(S_i,s_{0 i}, \rightarrow_i)$, and $\xrightarrow{b_j}_j$
-        is a transition of the hole $j$, for any action $b_j$ in the
-        sort $Sort_j$. \Pred\ is a predicate
-	over the different variables of the
-	terms, labels, and states $s_i$, $b_j$, $s$, $v$. \Post\ is a set of equations that 
-	hold \emph{after the open transition}, they are represented as a substitution of the 
-	form $\{x_k\gets e_k\}^{k\in K}$ 
-	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
-	variables of the open transition.
-\end{definition}
-
-\begin{example}\emph{An open-transition.}
-  \label{OT:enable-composed}
-  The \texttt{EnableCompL} pNet of Fig. \ref{schema:enable-composed} has 2 controllers and 2 holes. One of its possible open-transition is:
-
- \smallskip
- $  OT_2  = \openrule{
-                       0 \xrightarrow{\delta}_{C_3} 1 ~~
-                            0 \xrightarrow{l}_{C_4} 0  ~~                 
-                            \xrightarrow{\delta(x4)}_P ~~
-                            \xrightarrow{accept(x4)}_Q 
-                      }
-  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
-    {A1_0 \xrightarrow{\underline{\delta(x4)}} A1_1}
-  $
-\end{example}
-
-\begin{definition}[Open automaton]
-	\label{def:open-automaton}
-	An \emph{open automaton} is a structure\\ $A =
-	<LTS_i^{i\in I},J,\mathcal{S},s_0,\mathcal{T}>$ where:
-	\begin{itemize}
-		\item[$\bullet$]  $I$ and $J$ are  sets of indices,
-		\item[$\bullet$]  $LTS_i^{i\in I}$ is a family of LTSs,
-		\item[$\bullet$]   $\mathcal{S}$ is a set of states and $s_0$ an initial state
-		among $\mathcal{S}$,
-		\item[$\bullet$] $\mathcal{T}$ is a set of open transitions and for each
-		$t\in \mathcal{T}$ there exist $I'$, $J'$ with $I'\subseteq I$, $J'
-		\subseteq J$, such that $t$ is an open transition over $LTS_i^{i\in I'}$, $J'$,
-		and  $\mathcal{S}$.
-
-	\end{itemize}
-\end{definition}
-
-%
-%Then the semantics of a pNet is characterized by a set of {\em open
-%transitions}, where the hypotheses on process parameters are
-%replaced by 1) transitions of the pLTSs at the leaves, and 2) formal
-%hypotheses on the transitions of the holes. A {\em predicate} is used
-%to relate the parameters and names appearing in the actions of the
-%leaves and the holes involved in the rules, but also appearing in  the resulting action.
-
-\begin{definition}[States of open pNets]\label{def-states}
-  A state of an open pNet is a tuple (not necessarily finite) of the
-  states of its leaves (in which we denote tuples
-  in structured states as $\triangleleft\ldots\triangleright$ for better readability).
-
-  For any pNet p, let $\overline{Leaves} = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be the set of pLTS at its leaves,
-  then $States(p) = \{\triangleleft s_i^{i\in L}
-  \triangleright| \forall i\in L. s_i \in S_i\}$.
-A pLTS being its own single leave:
-  $States(\mylangle S,s_0, \to\myrangle) = \{\triangleleft s \triangleright| s \in S\}$.
-
-The initial state is defined as:
-$InitState(p) = \triangleleft {{s_i}_0}^{i\in L}  \triangleright$.
-\end{definition}
-
-%% \begin{example} \emph{State of a pNet}
-%%   The states of pNet \texttt{EnableCompL} are:
-%%   $\triangleleft 00 \triangleright, \triangleleft 10 \triangleright, \triangleleft 11 \triangleright$
-%% \end{example}
-
-\paragraph{Predicates:}
-Let
-$\mylangle\overline{\pNet},\overline{S},\symb{SV}_k^{k\in K} \myrangle$
-be a pNet. Consider a synchronisation vector $SV_k$, for $k\in K$. We define a
-predicate $\Pred$ relating
-the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
-\[\Pred(SV_k, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow
-\begin{array}{l}
-\exists {(a'_i)}^{i\in I},
-{(b'_j)}^{j\in J},v'.\, SV_k={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v'
-\\~~\land
-\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v'
-\end{array}\]
-In any other case (if the action families do not match or if there is no valuation of
-variables such that the above formula can be ensured) the predicate is undefined.
-
-This definition is not constructive but it is easy to build the predicate constructively
-by brute-force unification of the sub-pNets
-actions with the corresponding vector actions, possibly followed by a simplification
-step.
-
-We build the semantics of open pNets as an open automaton where LTSs are the pLTSs at
-the leaves of the pNet structure, and the states are given by 
-Definition~\ref{def-states}. The open transitions first
- project the global state into states of the leaves, then apply
-pLTS transitions on these states, and compose them with the sort of the holes. %The pNet
-%structure does not appear in the open-automaton, only the
-%set of Holes and the set of Leaves.
-The semantics   regularly instantiates \emph{fresh} variables, and uses a
-\emph{clone} operator that clones a term replacing each variable with a
-fresh one.
-
-\begin{definition}[Operational semantics of open pNets]
-	\label{def:operationalSemantics}
-	The semantics of a pNet $p$ is an open automaton $A = <Leaves(p),J,\mathcal{S}, s_0,
-	\mathcal{T}>$ where:
-	\begin{itemize}
-		\item $J$ is the indices of the holes: $Holes(p)= H_j^{j\in J}$.
-		%  \item $\overline{L}^L = Leaves(p), \overline{H}^J = Holes(p)$
-		\item $\overline{\mathcal{S}} = States(p)$ and $s_0 = InitState(p)$
-		\item $\mathcal{T}$ is the smallest set of open transitions
-		satisfying the rules below:
+   \item[$\bullet$] $prefix$ is the name of variable action composed with an internal name. So far the internal name can be  sva (SV action), ra (result action), hb (hole behavior).
+   \item[$\bullet$] $tree index$ is the index of the node in the tree-like structure of the pNet.
+   \item[$\bullet$] $counter$ is the current value of the corresponding counter.
 \end{itemize}
 
-	The rule for a pLTS $p$  checks that the guard 
-	is verified and transforms assignments into post-conditions:
-
-	\begin{description}
-		\item[{\bf Tr1:}]
-		$\inferrule
-		{ s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
-					J}\rangle} s'\in \to  }
-		{ p = \mylangle  S,s_0, \to \myrangle
-			\models
-			\inferrule*[myfraction=\reddottedrule]
-			{\{s \xrightarrow{\alpha}_p s'\} ,\emptyset ,
-			e_b,\left\{x_j\gets e_j\right\}^{j\in J}}
-			{\ostate{s} \xrightarrow{\alpha} \ostate{s'}}
-		}
-		$
-	\end{description}
-%	Note that this note is greatly simplified by the fact that variables are local to 
-%	thread; introducing global state variables or accepting loops to the same 
-%	state would 
-%	require to reason 
-%	on the scope of 
-%	each variables, and to introduce additional variables to handle the several occurence 
-%	of the same pLTS variable in the predicates. Indeed the constraints on pLTS 
-%	transitions 
-%	ensure that the same variable never appears both on the left and on the right of the 
-%	equations of a predicate.
-
-	The second rule deals with pNet nodes: for each possible
-	synchronisation vector applicable to the rule subject, the premisses
-	include one {\em open transition} for each sub-pNet involved, one possible
-	{\em action} for each Hole involved, and the predicate relating these
-	with the resulting action of the vector.
-	A key to understand this rule is that the open transitions are
-	expressed in terms of the leaves and holes of the pNet structure,
-	i.e. a flatten view of the pNet: e.g. $L$ is the index set of the
-	Leaves, $L_k$ the index set of the leaves of one subnet, so all $L_k$
-	are disjoint subsets of $L$. Thus the states in the open transitions,
-	at each level, are tuples including states of all the
-	leaves of the pNet, not only those involved in the chosen
-	synchronisation vector.
-
-	\begin{description}
-		\item[{\bf Tr2:}]
-	\end{description}
-
-	\noindent
-    $\inferrule
-    {k\!\in\! K \\ SV\!\!= \!clone(SV_k) \!=\! \alpha_m^{m \in I_k\uplus J_k} \!\to\! 
-    \alpha'_k \\
-    	Leaves(p) \!=\! \pLTS_l^{l\in L} \\    	
-    	\forall m\in I_k.
-    	\pNet_m \models
-    	\inferrule*[myfraction=\reddottedrule]
-    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
-    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
-    	{\ostate{s_{i}^{i \in L_m}} \xrightarrow {v_m}
-    		\ostate{s_{i}^{\prime\ i \in L_m}}}
-    	%\land
-    	%Leaves(\pNet_m) = \overline{pLTS}^{L_k})
-    	\\
-    	I' = \biguplus_{m\in I_k}\!\! I_m'
-    	\\ J' = \biguplus_{m\in I_k}\!\! J'_m \uplus J_k 	\\
-    	\Pred = \bigwedge_{m\in I_k}\!\! \Pred_m \land
-    	\Pred(SV,a_i^{i\in I_k},b_j^{j\in J_k},v)\\
-    	\forall j\!\!\in\!\! J_k. {\tt 
-    		fresh}(b_j) \\ {\tt fresh}(v) \\ 
-    	\forall i\in
-    	L\backslash I'.\,s'_i=s_i 
-    }
-    {p = \mylangle \pNet_i^{i\in I}, S_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle
-    	\models
-    	{\inferrule*[myfraction=\reddottedrule]
-    		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I^\prime},
-    		\{\xrightarrow{b_j}_j\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_k} 
-    		\Post_m}
-    		{\ostate{s_i^{i\in L}} \xrightarrow {v}
-    			\ostate{s_i^{\prime i\in L}}}
-    	}
-    }
-    $
-
-	\medskip
-
-\end{definition}
-%
-
-\begin{example} \emph{Using the operational rules to compute
-    open-transitions}
-  In Fig. \ref{usingrules:OT2} we show the deduction tree used to construct and prove the 
-  open transition $OT_2$ of \texttt{EnableCompL} (see example page \pageref{OT:enable-composed}).
-  The rule uses TR1 for the $\delta$ transition of $C_3$, for the $l$ transition of $C_4$, then combines the result using the $a_4$ vector of the bottom pNet node, and the $\underline{\delta(x)}$ vector of the top node.
-
-\begin{figure}[tb]
-\begin{mathpar}
-  \small
-  \inferrule
-    {\inferrule
-        {0 \xrightarrow {\delta}_{C_3} 1}
-        {C_3
-          \models
-            \openrule{
-              0 \xrightarrow {\delta}_{C_3} 1,\,
-              \{\xrightarrow{\delta(x_1)}_P\},\,
-              v_1=\delta(x_1)}
-                      {\ostate{0}\xrightarrow{v_1}\ostate{1}}
-        }\\
-%      \sm{fresh}v         \\
-      \inferrule%*[right={L_1}]
-        {
-%          \sm{fresh}{a_Q} \\
-          \inferrule
-              {0 \xrightarrow{l}_{C_4} 0}
-              % {\ostate{0}\xrightarrow{l}\ostate{0}}
-              {C_4
-                \models
-                \openrule{
-                      0 \xrightarrow l_{C_4} 0,\,
-                      \sm{Pred}_{C_4}}
-                      {\ostate{0}\xrightarrow{l}\ostate{0}}
-              }
-        }
-        {
-          \textrm{Q>>R}\models
-              \openrule
-                  { 0 \xrightarrow {l}_{C_4} 0,\,
-                    \{\xrightarrow{acc(x_2)}_Q\},\,
-                    \ v_2=acc(x_2)
-                  }
-                  {\ostate{0}\xrightarrow{v_2}\ostate{0}}
-        }   
-    }
-    {
-     \textrm{P>>(Q>>R)}
-     \models
-     \openrule
-         { 0 \xrightarrow{\delta}_{C_3} 1, \\ 0 \xrightarrow{l}_{C_4} 0,\\
-           \{\xrightarrow{\delta(x)}_P,\,\xrightarrow{acc(x)}_Q\}, \\
-            a_3=v_1 \wedge v=a_3 \wedge x_1=x_2
-           }
-         {\ostate{00} \xrightarrow{v} \ostate{10}}
-      }\vspace{-4ex}
-\end{mathpar}
-  \caption{Proof of transition $OT_2$ (with interaction of processes $P$ and $Q$) for ``P>>(Q>>R)''}
-  \label{usingrules:OT2}
-\end{figure}
-
-\end{example}
-
-Note that while the scenario above is expressed as a single
-instantiation of the possible behaviours, the constructions below are
-kept symbolic, and each open-transition deduced expresses a whole family of
-behaviours, for any possible values of the variables.
-
-\paragraph{Variable management.}
-The variables in each synchronisation vector are considered local:
-for a given pNet expression, we must have fresh local variables for
-each occurrence of a vector (= each time we instantiate rule
-Tr2). Similarly the state variables of each copy of a
-given pLTS in the system, must be distinct, and those created for each
-application of Tr2 have to be fresh and all distinct. 
-This will be implemented within the open-automaton generation algorithm,
-e.g. using name generation using a global counter as a suffix.
-
-\subsection{Computing and using open automata}
-In this section we present an algorithm to construct the open
-automaton representing the behaviour of an open pNet, and we prove that
-under reasonable conditions this automaton is finite.
-
-\TODO{Refine the algorithm description}
-
-\begin{algorithm}[Behavioural semantics of open pNets: Sketch]
-This is a standard residual algorithm over a set of open-automaton
-states, but where transitions are open transitions
-constructively ``proven'' by deduction trees.
-
-1) Start with a set of unexplored states containing the initial state
-of the automaton, and an empty set of explored states.
-
-2) While there are unexplored states:
-
-2a) pick one state from the unexplored set and add it to the explored
-set. From this state
-build all possible deduction trees by application of the structural
-rules Tr1 and Tr2, using all \ERIC{applicable} combinations
-of synchronisation vectors.
-
-2b) For each of the obtained deduction trees, extract the resulting
-open-transition, with its predicate and \Post\ assignments by exploring the structure of 
-the pNet.
-
-2c)
-\ERIC{The predicate is submitted to Z3 for checking satisfiability. If it is NOT stisfiable, the resulting OT is discarded. This will minimize the number of
-resulting transitions, and potentialy prune the search-space.}
-
-2d)
-\ERIC{Optionally, simplify the predicate by eliminating the unnecessary intermediate variables, that were produced as fresh local variables of synchronisation vectors, and fresh result variables of intermediate OTs.
-In the resulting predicate the only significant variables are :\\
-- the input variables of pLTS transitions\\
-- the actions of holes\\
-- the result action at toplevel.}
-
-For each open-transition,  add the transition in the outgoing transitions of
-the current state, and add the
-resulting state in the unexplored set if it is not already in the
-explored set.
-
-%3) this ends with the "while" from step 2, when we have no more
-%unexplored set.
-\end{algorithm}
-
-To have some practical interest, it is important to know when this
-algorithm terminates. The following theorem shows that an open-pNet
-with finite synchronisation sets, finitely many leaves and
-holes, and each pLTS at leaves having a finite number of states and
-(symbolic) transitions, has a finite automaton:
-
-\begin{theorem}[Finiteness of open-automata.]\\
-Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
-  J}$, if the sets $L$ and $J$ are finite, if the synchronisation vectors of all pNets 
-  included in  $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ 
-  are finite, and if
-$\forall i \in L.\, finite{(states(pLTS_i))} \text{ and } pLTS_i$
-has a finite number of state variables, then Algorithm 1 terminates
-and produces an open automaton 
-$\mathcal{T}$ with finitely many states and transitions.
-
-% Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in
-%     K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
-%   J}$,
-% build its semantics as in algorithm 1.
-
-% We have:
-
-% $$ finite{(L)} \land finite{(J)} \land \forall i \in L finite{(\{s_i\})}
-%   \to finite{(\mathcal{T})}$$
-\end{theorem}
-
-\section{Implementation}
-
-\TODO{Xudong: Detailed description of the implementation}
-
-\ERIC{
-=> Context VCE, ref to FASE paper\\
-=> Current prototype: programatic creation of pNet objects, through the pNet API in VCE. On the middle term, this should be compiled from some language or graphical formalism.\\
-=> Open transitions are computed as a direct implementation of the algorithm above.
-Steps 2a-2b are merged: at each pNet node, after application of rule Tr2, the resulting OT is built from the premisses, without explicitely constructing the deduction tree.
-\\
-=> Variable names are generated for all ``fresh'' and ``clone''
-operations, using structured variable names ensuring uniqueness of
-fresh names, but also reasonable readability of these names for
-debugging purposes.\\
-=> Assignements\\
-=> Satisfiability check is done only at toplevel of the deduction tree construction.
-An alternative would be to submit the satisfiability check to the SMT solver at each level of the tree construction, potentialy reducing the overall number of combinations.
-But submission to the SMT engine is costly, and more complexity analysis is required before deciding if this would be worthwhile.\\
-=> Simplification is not yet implemented. It is not strictly required for the Open Automaton construction, but it will be critical later for predicate comparison in the bisimulation algorithm.}
-
-\TODO{Xudong: full result of the tool execution on the running example}
-
-\section{Conclusion and Discussion}
-\label{section:conclusion}
-
-\bibliographystyle{lncs/splncs}
-
-% \bibliography{oasis,biblio}
-\bibliography{biblio}
-
-% \newpage
-% \appendix
-
 \end{document}

### 2017-02-09 2016-Weak-FH-Bisim/WeakBisim.tex
renaming in transitivity

@@
 Let $\mathcal{R}''$ be the relation: 
-\[\mathcal{R}'' = \{(s^1,s^3|\Pred\,'')|\,\Pred\,''=\bigvee_{ \begin{array}{l}
+\[\mathcal{R}'' = \Big\{(s^1,s^3|\Pred\,''\phi)\Big|\begin{array}{l}
+\displaystyle\Pred\,''=\bigvee_{ \begin{array}{l}
 (s^1,s^2|\Pred)\in\mathcal{R}\\ (s^2,s^3|\Pred\,')\in\mathcal{R}' 	
 \end{array}
-}\,\Pred\land\Pred\,'\}\]
+}\,\Pred\land\Pred\,'\\
+\land~ \phi \text{ renames variables of $\mathcal{T}_2$ into fresh variables}
+\end{array}\Big\}\]
 
@@
 values of $s^2$ are collected by a disjunction. 
+Free variables are renamed to avoid further clashes with variables of $\mathcal{T}_2$; in 
+practice, because having name clashes between different terms of the disjunction is not 
+an issue, there is no need to have a different $\phi$ for each predicate, and we will use 
+a global renaming $\phi$ in the following.
 
@@
 For any open transition $OT$ in $\mathcal{T}_1$ originating from $s^1$:
-Additionally we have $\Pred\,'' = \bigvee_{p\in P} \Pred_p\land\Pred_p\,'$.
+Additionally we have $\Pred\,'' = (\bigvee_{p\in P} \Pred_p\land\Pred_p\,')\phi$.
 \begin{mathpar}
@@
  the set of states relating ${s^{1}}'$ and $s^{3}_{pxy}$.
-Consequently, for all $p$, $x$, $y$, $\Pred_{target_{px}}\land 
-\Pred_{target_{pxy}}\implies 
+Consequently, for all $p$, $x$, $y$, $(\Pred_{target_{px}}\land 
+\Pred_{target_{pxy}})\phi\implies 
 \Pred\,'_{target_{pxy}}$ (this is one element of the  disjunction defining the 
 predicate 
-relating ${s^{1}}'$ and $s^{3}_{pxy}$ in the definition of $\mathcal{R}''$).
+relating ${s^{1}}'$ and $s^{3}_{pxy}$ in the definition of $\mathcal{R}''$, note the use 
+of the global substitution $\phi$ ensuring that $\Pred\,'_{target_{pxy}}$ does not use 
+the variables of $\mathcal{T}_2$).
 
@@
 
-Additionally, the Post renamings do not modify the predicates that only use non-renamed 
-variables, and because of the domain of the renamings:\\
-$\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\land 
-\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
+Additionally, the Post substitutions do not modify the predicates that only use 
+non-substituted 
+variables, and because of the domain of the substitutions:\\
+$(\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\land 
+\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}})\phi\\
+%
 = 
-\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land 
-\Pred_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
-\implies\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
-= \Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}} $
-
-This allows us to conclude: using $\Pred\,'' = \bigvee_{p\in P} \Pred_p\land\Pred_p\,'$ 
-and the assertions above we obtained the needed property.
+(\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land
+\Pred_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}) 
+\phi\\
+%
+\implies\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}\phi}}
+\subst{\Post_{OT_{pxy}}}\\
+%
+= 
+\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\subst{\Post_{OT_{px}}\phi}\\
+ $
+Finally, gathering the previous results:
+
+$\Pred\,'' \land \Pred_{OT}\\
+\hspace{1cm} \implies\!\!\! \bigvee_{p\in P}(\Pred_p \land 
+\Pred_{OT}\land\Pred\,'_p)\phi\\
+\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
+\left( \forall j. b_j=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
+\land v\!=\!v_{pxy} \land
+\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\subst{\Post_{OT_{px}}\phi}\right)
+$
+
+This is the expected property except for the $\subst{\Post_{OT_{px}}\phi}$ however, now, 
+this substitution only modifies internal variables of $\Pred\,'_{target_{pxy}}$ that are 
+part of no other term of the assertion (in particular neither $\Pred\,''$ nor 
+$\Pred_{OT}$), it can thus safely be removed to obtain the needed property.
 

### 2017-02-10 2016-Weak-FH-Bisim/WeakBisim.tex
transitivity V2 !

--- 2017-02-08 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 $(s^2,s^3|\Pred\,')$.
+We use $\fv$ a function returning the free variables of a term/automaton.
 
 Let $\mathcal{R}''$ be the relation: 
-\[\mathcal{R}'' = \{(s^1,s^3|\Pred\,'')|\,\Pred\,''=\bigvee_{ \begin{array}{l}
+\[\mathcal{R}'' = \Big\{(s^1,s^3|\Pred\,''\phi)\Big|
+\displaystyle\Pred\,''=\bigvee_{ \begin{array}{l}
 (s^1,s^2|\Pred)\in\mathcal{R}\\ (s^2,s^3|\Pred\,')\in\mathcal{R}' 	
 \end{array}
-}\,\Pred\land\Pred\,'\}\]
+}\!\!\!\!\!\exists \phi.\begin{array}[t]{l} (\Pred\land\Pred\,')\phi\\
+\land \fv((\Pred\land\Pred)\phi)\subseteq \fv(\mathcal{T}_1)\cup\fv(\mathcal{T}_3)
+\\
+\land \dom(\phi)\subseteq \fv(\mathcal{T}_2)
+\end{array}\Big\}\]
+
+\TODO{is it satisfactory as a notion of transitive composition? It would be easy to 
+extend it a bit to allow having several substitutions for the same s2, eg one that works 
+for different values of variables in T1 and T3. It would make the notations more complex 
+but it would be OK. I do not think I can do more than that}
 
@@
 values of $s^2$ are collected by a disjunction. 
+Finally, a substitution should ensure that the 
+free variables of the predicates are only the ones of $\mathcal{T}_1$ and 
+$\mathcal{T}_1$. This substitution somehow matches the two predicates by eliminating the 
+free variables.
 
@@
 $\mathcal{T}_2$ relating $s^1$ and $s^3$, let $(s^2_p)^{p\in P}$ be this family.  
-
 For any $p\in P$ by definition of $\mathcal{R}''$,
-$(s^1,s^2_p|\Pred_p)\in\mathcal{R}$,  and $(s^2_p,s^3|\Pred\,'_p)\in\mathcal{R}$. We have 
+$(s^1,s^2_p|\Pred_p)\in\mathcal{R}$,  and $(s^2_p,s^3|\Pred\,'_p)\in\mathcal{R}$. 
+Additionally we have $\Pred\,'' = (\bigvee_{p\in P} \Pred_p\land\Pred_p\,'\phi_p)$.
+We have 
 the 
@@
 For any open transition $OT$ in $\mathcal{T}_1$ originating from $s^1$:
-Additionally we have $\Pred\,'' = \bigvee_{p\in P} \Pred_p\land\Pred_p\,'$.
+
 \begin{mathpar}
@@
 (s^{2}_x,s^{3}_{pxy}|\Pred_{target_{pxy}})\in \mathcal{R}'$; and  \\
-$\Pred\,'_p \land \Pred_{OT_x}\\
+$\Pred\,'_p \land \Pred_{OT_{px}}\\
 \hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
@@
  the set of states relating ${s^{1}}'$ and $s^{3}_{pxy}$.
-Consequently, for all $p$, $x$, $y$, $\Pred_{target_{px}}\land 
-\Pred_{target_{pxy}}\implies 
-\Pred\,'_{target_{pxy}}$ (this is one element of the  disjunction defining the 
+Consequently, for all $p$, $x$, $y$,\\
+ $\left(\exists \phi'.\,(\Pred_{target_{px}}\land 
+\Pred_{target_{pxy}})\phi'\land \fv((\Pred\land\Pred)\phi')\subseteq 
+\fv(\mathcal{T}_1)\cup\fv(\mathcal{T}_3)\right)\implies 
+\Pred\,'_{target_{pxy}}$ \\
+This is one element of the  disjunction defining the 
 predicate 
-relating ${s^{1}}'$ and $s^{3}_{pxy}$ in the definition of $\mathcal{R}''$).
+relating ${s^{1}}'$ and $s^{3}_{pxy}$ in the definition of $\mathcal{R}''$.
 
@@
 
-Additionally, the Post renamings do not modify the predicates that only use non-renamed 
-variables, and because of the domain of the renamings:\\
-$\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\land 
-\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
+Additionally, the Post substitutions only have an effect on the  predicates that  use 
+some of the 
+substituted 
+variables, and because of the domain of the substitutions we have:\\
+$(\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\land 
+\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}})\phi\\
+%
 = 
-\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land 
-\Pred_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
-\implies\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
-= \Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}} $
-
-This allows us to conclude: using $\Pred\,'' = \bigvee_{p\in P} \Pred_p\land\Pred_p\,'$ 
-and the assertions above we obtained the needed property.
+(\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land
+\Pred_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}) 
+\phi\\
+%
+= 
+((\Pred_{target_{px}}\land
+\Pred_{target_{pxy}})\subst{\Post_{OT_{px}}}\phi) 
+\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\\
+%
+\implies\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}
+\subst{\Post_{OT_{pxy}}}\\
+ $
+Finally, gathering the previous results, and using the fact that only variables of 
+$\mathcal{T}_2$ are changed by $\phi$ substitutions:
+
+$\Pred\,'' \land \Pred_{OT}\\
+\hspace{1cm} \implies\!\!\! \bigvee_{p\in P}(\Pred_p \land 
+\Pred_{OT}\land\Pred\,'_p)\phi\\
+\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
+\left( \forall j. b_j=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
+\land v\!=\!v_{pxy} \land
+\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)
+$
+
+This is the expected property.
 

### 2017-02-15 2016-Weak-FH-Bisim/WeakBisim.tex
indices in bisim figure, and lotos equivalence exempl rules

@@
 
- \TODO{Eric: il reste des petits bugs genre $s^{2'}_x$ plutot que
-   $s^{2}_x$}
+% \TODO{Eric: il reste des petits bugs genre $s^{2'}_x$ plutot que
+%   $s^{2}_x$}
 
@@
 \TODO{Eric: ask Elie, Hubert or others about interesting weak
-  equationnal theories for Lotos -- DONE, waiting for answer...}
+  equationnal theories for Lotos -- DONE, no answer..., so I got some examples from \cite{Lotos:ISO}}
 
@@
   ``operators'' -- DONE!}
+
+Possible Lotos small examples:
+
+Strong bisim:\\
+\centerline{hide \{g\} in a;B  ==  a; hide \{g\} in B  iff gatename(a)$\neq$g}\\
+\centerline{hide \{g\} in a;B  ==  i; hide \{g\} in B  iff gatename(a)$=$g}
+
+Weak congruence:\\
+\centerline{a;i;B == a;B}\\
+\centerline{B[]i;B == i;B}\\
+and many others, often not easy to express without syntax for set operations.
+
+Weak equivalence:\\
+\centerline{i;B == B}
 

### 2017-02-16 2016-Weak-FH-Bisim/WeakBisim.tex
Lotos laws

@@
 Strong bisim:\\
+1) Hiding:\\
 \centerline{hide \{g\} in a;B  ==  a; hide \{g\} in B  iff gatename(a)$\neq$g}\\
 \centerline{hide \{g\} in a;B  ==  i; hide \{g\} in B  iff gatename(a)$=$g}
+2) Disabling:\\
+\centerline{B1[>(B2[>B3) == (B1[>B2)[>b3}\\
+\centerline{(B1[>B2)[]B3 == B1[>B2}\\
+\centerline{B[>stop == B}\\
+\centerline{stop[>B == B}\\
+\centerline{exit(...)[>B == exit(...)[]B}\\
+3) Enabling:\\
+\centerline{B1>>(B2>>B3) == (B1>>B2)>>b3}\\
+\centerline{B>>stop == B|||stop}\\
+\centerline{stop>>B == stop}\\
+\centerline{exit>>B == i;B}\\
+4) Choice:\\
+\centerline{B1[](B2[]B3) == (B1[]B2)[]b3}\\
+\centerline{B1[]B2 == B2[]B1}\\
+\centerline{B[]stop == B}\\
+\centerline{B[]B == B}\\
+
+5) Others:\\
+\centerline{B1|[]|B2 == B1|||B2}\\
 
@@
 \centerline{B[]i;B == i;B}\\
-and many others, often not easy to express without syntax for set operations.
+and many others, often not easy to express without syntax for set operations,
+like e.g.:
+\centerline{}
 

### 2017-02-27 2017-Xudong-SMT/OpenPNets-SMT.tex
OpenPNets-SMT.tex modified
Add some stuff into the 5th section.

@@
 
-\TODO{Xudong: Detailed description of the implementation}
+\TODO{
+Xudong: Detailed description of the implementation\\\\
+5.1 Generation of the Open Transition\\\\
+5.1.1 fresh variable\\\\
+The variable in each SV are considered local, so does the variable of an open transition such as its hole behavior and its result action.
+So we want rename them to make them unique, while we also hope them readable. The fresh variable has a confirmed format.
+As pNets has a tree-like structure, we give every node of the pNets a tree index.
+And give them some counters to count the current times the SV, Hole or subnet is used, and the number of possible OT generated.
+\\\\
+| format of fresh variable |\\\\
+5.1.2 predicate generation\\\\
+Combining, present all the possible working status of subnets. \\
+Mixing, match the elements of the combination to match the elements of the SV one by one to generate terms of a predicate.\\\\
+5.1.3 assignment\\\\
+Management of state variables.\\
+Translating assignments into predicate terms.\\\\
+5.2 Pruning the unsatisfiable results\\\\
+Interaction with Z3: pNets module ---input--> Z3 module [JAVA API]\\\\
+5.2.1 presentation\\\\
+5.2.2 checking satisfiability\\\\
+After we get the result OTs, for each result OT, declare the variables and assertions in the Java API. Conduct checking method and get the result.\\
+}
 
@@
 
-\TODO{Xudong: full result of the tool execution on the running example}
+\TODO{
+Xudong: full result of the tool execution on the running example\\\\
+Open Automata of the CCS example.
+}
 

### 2017-03-01 2017-Xudong-SMT/OpenPNets-SMT.tex
Commit test
Have chosen a color.

@@
 \newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
+\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
+\newcommand{\QIN}[1]{\textcolor{airforceblue}{#1}}
 \newcommand{\coloncolon}{{:\hspace{-.2ex}:}}
@@
 
-\TODO{
-Xudong: Detailed description of the implementation\\\\
+\TODO{Xudong: Detailed description of the implementation}
+\QIN{
+\\
 5.1 Generation of the Open Transition\\\\
@@
 }
-
 \ERIC{

### 2017-03-09 2017-Xudong-SMT/OpenPNets-SMT.tex
Write the sections in OpenPNets-SMT.
Finish the CCS running example and the definition of presentation.

@@
 \newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
-\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
+\definecolor{airforceblue}{rgb}{0.26, 0.44, 0.56}
 \newcommand{\QIN}[1]{\textcolor{airforceblue}{#1}}
@@
 
-\section{Running Example(s)}
+\section{Running Examples}
+\TODO{Graph of two examples: CCS a.P||b.Q [DONE] and LOTOS (P>>Q)>>R}
+
+\TODO{Description of two examples: CCS a.P||b.Q [DONE] and LOTOS (P>>Q)>>R}
+
+\QIN{There are several former papers already have illustrated many examples in closed pNets show that pNets can properly simulate the original construct.
+In this section, we encode the operators from other algebras into the pNets present the feature of the open pNet.
+They will be the running examples in the whole paper.
+}
+
+\subsection{Operators from Classical Process Algebra}
+\QIN{First example we choose is a formula $a.P||b.Q$, composing the prefix operator and parallel operator of CCS. 
+In Fig. 1, we show the encoding of this CCS formula. The pNet has a tree-like structure. }
+
+\QIN{The root node of the tree PN1 is the top level of the pNet structure.
+It acts as the parallel operator.
+There are two subnodes, also called subnets, noted PN2 and PN3.
+Their behaviors are synchronized in their parent PN1 according to a set of synchronization vectors, synchronizing input and output action from these two subnets to give out a silent action $\tau$ or just making the action become visible on this level when one of subnets is not working.
+}
+
+\QIN{Its subnets act as the prefix operator, so these pNets have a same structure.
+There is a pLTS and a hole in each pNet node.
+The pLTS encoding the controller of the pNet.
+Collaborating with the synchronization vectors, the controller manages the specific behavior of the pNet.
+Such as in the pLTS C1, the only action start from the initial state is $a$ and there is a synchronization vector transmits it to the outside, it makes the first action always be $a$.
+A guard is added as a constraint into its notation in that we want this vector to only apply to the first action of C1.
+And another synchronization vector keeps the following actions come from the process $P$.
+The action of the process $P$ is uncertain here, so the hole is used as a process parameter of the pNet to present the behavior of the process $P$.
+that is what shows the open property.}
+
+\subsection{Open pNet with Assignments in Leaves}
+
+\begin{figure}[t]
+
+\begin{minipage}{6cm}
+  \includegraphics[width=\linewidth]{XFIG/CCS1}
+  \caption{The pNet encodings for CCS formula}  \label{schema:ccs-pnets}
+\end{minipage}
+\hspace{2mm}
+\begin{minipage}{6cm}
+  \includegraphics[width=\linewidth]{XFIG/Enable1}
+  \\[1.3ex]
+  \includegraphics[width=\linewidth]{XFIG/Enable2}
+  \caption{Two pNet encodings for  Enable }  \label{schema:enable-pnets}
+\end{minipage}
+
+\end{figure}
 
@@
 
+\subsection{Presentation of algebra}
+\QIN{Before the encoding, the presentation of the pNet should be given first. We can divide the presentation into two parts:}
+\begin{itemize}
+	\item Sorts: Constants sets of the algebra, types of the data and actions.
+	\item Operators: Operators comes from other algebras,  constructors for the parameterized actions.
+\end{itemize}
+
+\paragraph{Sorts}
+\QIN{Ownership of the variables and constants in a pNet acting as actions or data is probably various.
+Sorts are represented by their name.
+The sort of actions is built by the constant actions.
+For example, let $CCSAct$ be the only set of actions of the CCS running example.
+Obviously, $CCSAct$ contains constant actions $l$, $r$ in the pLTSs.
+Sorts here act as sets of actions for pNet, pLTS or holes.
+Intuitively, Sorts of data and actions are completely independent.
+Sorts of the data like a type of them could be integer, boolean or a customized type.
+Sorts for integer and boolean are implicitly declared.}
+
+\paragraph{Operators}
+\QIN{Usually we need introduce the expressions from other algebra when encoding the algebra into pNets.
+So that is needed to know about the input and output of the operators used in the expressions from those algebra.
+The input and output should belong to the sorts on the pNet.
+When there are $k$ sorts in this pNet, the structure of a $n$-ary operator is vector as $< Sort_{i_1}, ...
+, Sort_{i_n} > \rightarrow Sort_j , i_1 , ...
+, i_n, j \in [0..k] $.}
+
+\paragraph{Extension of other algebras}
+\QIN{Variable, constant are treated as a kind of expression together with the expression using operator.
+Operators can be categorized into unary operator, binary operator and N-ary operator, that make it possible to present operator from other algebras.
+In Fig .6, we show the Expression class we improved to enable user to extend other algebras in the pNet.
+There are classes implementing three kinds of expression extend the original  Expression class.
+From these three classes, more classes are extended using the operators coming from other algebra such as CCS and LOTOS}
+
+\begin{figure}[t]
+  \includegraphics[width=\linewidth]{XFIG/Expression}
+  \caption{The architecture of Expression class}  \label{schema:expression-pnets}
+\end{figure}
+
 \subsection{Computing and using open automata}
@@
 5.1.2 predicate generation\\\\
-Combining, present all the possible working status of subnets. \\
-Mixing, match the elements of the combination to match the elements of the SV one by one to generate terms of a predicate.\\\\
+Combining, present all the possible working status of subnets. 
+[pseudocode]
+\\
+Mixing, match the elements of the combination to match the elements of the SV one by one to generate terms of a predicate.
+[pseudocode]
+\\\\
 5.1.3 assignment\\\\

### 2017-03-13 2017-Xudong-SMT/pNetZ3paper.tex
Add algorithm of combining
See in pNetZ3paper.tex.

@@
 %\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{algorithm}[theorem]{Algorithm}
+\newtheorem{alg}[theorem]{Algorithm}
 %\newtheorem{remark}[theorem]{Remark}
@@
 \newcommand{\sm}[1]{\mbox{\boldmath\small #1}}
+\usepackage{algorithm} 
+\usepackage{algorithmicx} 
+\usepackage{algpseudocode}  
+\renewcommand{\algorithmicrequire}{\textbf{Input:}} 
+\renewcommand{\algorithmicensure}{\textbf{Output:}}
 
@@
 
-\begin{algorithm}[Operational Semantics Generation Algorithm of Open pNets]
+\begin{algorithm}
+\caption{Operational Semantics Generation Algorithm of Open pNets} 
+\begin{algorithmic}[1]
+
+\Require 
+\Ensure
+
+\State \Return
+
+\end{algorithmic} 
+\end{algorithm}
+
+%Combining is to generate all the possible matchings of the subnets' OTs (open transitions). The result list of the matched tuples called *combination*.
+% 1. Initialize the result list of OT tuples.
+% 2. Get one list of OTs. It's same as get OTs of one subnet.
+% 3. Add *null* into the list, it means this subnet does not work this time.
+% 4. Combine the rest subnets' OTs. Get the combination of the rest OTs.
+% 5. If there are OTs of the chosen list not be chosen, choose one OT.
+%      1. If there are tuples of the combination not be chosen, choose one tuple.
+%          1. Add the chosen OT into the tuple.
+%          2. Add the tuple into the result list, then do the recursion.
+% 6. Return the result list.
+\begin{algorithm}
+\caption{Combining}
+\begin{algorithmic}[1]
+
+\Require List $TR$ of result open transition lists from the subnets. 
+\Ensure All the possible combinations of open transitions.
+\State Initial an empty combination list $C$;
+\State Extract a list of open transitions $L$ from $TR$;
+\State Insert $null$ into $L$;
+\State Get the combinations $C'$ of the $TR$;
+\For{each $ot \in L$}
+	\For{each $tuple \in C'$}
+		\State Add $ot$ into $tuple$;
+		\State Add $tuple$ into $C$;
+	\EndFor
+\EndFor 
+\State \Return $C$;
+
+\end{algorithmic}  
+\end{algorithm}
+
+% Mixing is to match the combination of the subnets' open transitions, hole behaviors and result action with the SV (synchronization vector) to generate the possible predicates of the OT (open transition).
+At the same time, other parameters of the OT (global state, subnets' transitions, result action...) are also generated.
+Then the possible OTs of the pNet can be achieved.
+% 1. Initialize the combination through the method *combineOpenTransitions( )*.
+% 2. Initialize the result list.
+% 3. Get the number of subnets and holes. They are used to decide how many element of the SV should be matched with them.
+% 4. For all tuples of the combination.
+%      1. Invoke the *clone( )* method to generate the fresh SV.
+%      2.
+Match the elements of the tuple with the elements of the SV.
+If there is a *null* matched with a *not null* action, filter this matching.
+Add the result expression and the predicate of the subnets into the predicate.
+Generate the target global state correspondingly.
+%      3. Match the hole behaviors with the elements of the SV. The hole behavior could be *null*. Add the result expression into the predicate.
+%      4. Match the result action with the result action of SV. Add the result expression into the predicate.
+%      5. Add the predicate into the OT. Store the OT in the result list.  
+% 5. Return the result list of all the possible OTs.
+\begin{algorithm}
+\caption{Matching}
+\begin{algorithmic}[1]
+
+\Require 
+\Ensure
+
+\State \Return
+
+\end{algorithmic} 
+\end{algorithm}
+
+\end{document}
+
+\begin{document}
+
+\begin{alg}[Operational Semantics Generation Algorithm of Open pNets]
 Open transitions satisfying two rules:
@@
 
-\end{algorithm}
+\end{alg}
 

### 2017-03-14 2017-Xudong-SMT/pNetZ3paper.tex
Add algorithm and description.
Add algorithm and description of predicates generating.

@@
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
+\algnewcommand{\IfThenElse}[3]{\State \algorithmicif\ #1\ \algorithmicthen\ #2\ \algorithmicelse\ #3}% \IfThenElse{<if>}{<then>}{<else>}
 
@@
 
-\begin{algorithm}
-\caption{Operational Semantics Generation Algorithm of Open pNets} 
-\begin{algorithmic}[1]
-
-\Require 
-\Ensure
-
-\State \Return
-
-\end{algorithmic} 
-\end{algorithm}
+% Tr1 :
+% 1. Get the start state of the pLTS through the *TrackIndexImpl( )*.
+% 2. For all the transitions start with the start state.
+%       1. Get the target state of the transition. Generate the target global state according to the target state.
+%       2. Get the guard of the transition, add it into the predicate of the open transition. If there is no guard, add *true*.
+%       3. Store the generated open transition in the open transition list.
+% Tr2 :
+% It is more complicated, the SV (synchronization vector) need to be cloned, the variable actions need a fresh variable (renaming), and it need deal with the parameters come from the subnet.
+% 1. Initialize three counters for the subnet, hole behavior, result action and SV.
+% 2. Judge the type of all the subnets of the pNet.
+%       - If it is a pLTS, use the Tr1 recursively, store the open transitions list of the pLTS in the list of keeping subnets' open transitions.
+%       - If it is a hole, generate a new hole behavior for the open transition. 
+%           1. Count the number. The hole behaviour counter increase one.
+%           2. Build a fresh hole behavior through the method *fresh( )*.
+%           3. Generate the hole behavior with the type *ActionExpression*. Store it in the hole behaviors list of the open transition.
+%       - If it is a pNet, use the Tr2 recursively, store the open transitions list of the subnet in the list of keeping subnets' open transitions.
+% 3. Generate a new result action for the open transition.
+%       1. Count the number. The result action counter increase one.
+%       2. Build a fresh result action through the method *fresh( )*.
+%       3. Generate the result action with the type *ActionExpression*.
+% 4. For all SVs of the pNet.
+%       1.
+Invoke the *mixing( )* method.
+Match result action and the combination of the subnets' open transitions and hole behaviors with the SV to generate the predicates of the open transition.
+Then a possible open transition of the pNet is generated.
+%           - Every time the SV is chosen it need be cloned by the method *clone( )* and the cloned one is used for matching. 
+%           - Similarly, the variable elements of the combination are also need fresh variables.
+%       2. Store the open transition of the pNet in the opentransition list.
 
@@
 % 6. Return the result list.
+We first conduct combining.
+We make all the possible cases of the subnets' working status.
+The result action of a pLTS or a pNet is the external action of the node shows the working status of it.
+The hole whose behavior is uncertain doesn't have an exact external presentation of action.
+We only give a variable to each hole and treat it as hole behavior to suppose working status of the hole.
+Here should have a constraint that this variable belongs to the sort of hole.
+In every case, the hole behaviors are unchanged, so we only make all the combination of subnets' open transitions.
+
+Algorithm 1 shows the combining algorithm for enumerating all the possible combinations of open transitions. 
 \begin{algorithm}
@@
 \Require List $TR$ of result open transition lists from the subnets. 
-\Ensure All the possible combinations of open transitions.
-\State Initial an empty combination list $C$;
-\State Extract a list of open transitions $L$ from $TR$;
-\State Insert $null$ into $L$;
-\State Get the combinations $C'$ of the $TR$;
-\For{each $ot \in L$}
-	\For{each $tuple \in C'$}
-		\State Add $ot$ into $tuple$;
-		\State Add $tuple$ into $C$;
+\Ensure The list of all the possible combinations of open transitions $L_C$.
+\State Initial an empty combination list $L_C$;
+\State Extract a list of open transitions $L_{ot}$ from $TR$;
+\State Insert $null$ into $L_{ot}$;
+\State Get the combinations $L'_C$ of the $TR$;
+\For{each $ot \in L_{ot}$}
+	\For{each $C' \in L'_C$}
+		\State Add $ot$ into $C'$ to get a new tuple $C$;
+		\State Add $C$ into $L_C$;
 	\EndFor
 \EndFor 
-\State \Return $C$;
+\State \Return $L_C$;
 
@@
 \Require 
+The combination of subnets' open transitions $L_C$;
+The behaviors of the holes $B$;
+The set of synchronization vector $SV$.
 \Ensure 
-
-\State \Return
+The list of all the possible open transitions generated $L_{ot}$.
+\State Initial an empty result list $L_{ot}$;
+\For{each $C \in L_C$}
+	\For{each $sv \in SV$}
+		\State Clone the $sv$, the result is denoted as $sv'$;
+		\State Generate the fresh result action v;
+		\State Combine $C, B, v$ as a new tuple $<C, B, v>$;
+		\For{each $e_1 \in <C, B, v> \&\& e_2 \in sv'$}
+			\If{$(e_1\ is\ null\ \&\&\ e_2\ is\ not\ null)\ ||\ (e_1\ is\ not\ null\ \&\&\ e_2\ is\ null)$} 
+			\State Skip;
+			\Else 
+			\State Generate the $Pred$;
+			\EndIf
+		\EndFor
+		\State Generate the result open transition $ot$ with $Pred$;
+		\State Add the $ot$ into $L_{ot}$;
+	\EndFor
+\EndFor 
+\State \Return $L_{ot}$;
 

### 2017-03-15 2017-Xudong-SMT/pNetZ3paper.tex
Add content in section 5.
See pNetZ3paper.tex

--- 2017-03-13 2017-Xudong-SMT/pNetZ3paper.tex
@@
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
+\algnewcommand{\IfThenElse}[3]{\State \algorithmicif\ #1\ \algorithmicthen\ #2\ \algorithmicelse\ #3}% \IfThenElse{<if>}{<then>}{<else>}
 
 \begin{document}
-
-\begin{algorithm}
-\caption{Operational Semantics Generation Algorithm of Open pNets} 
-\begin{algorithmic}[1]
-
-\Require 
-\Ensure
-
-\State \Return
-
-\end{algorithmic} 
-\end{algorithm}
 
@@
 % 6. Return the result list.
+We first conduct combining.
+We enumerate all the possible cases of the subnets' working status.
+The result action of a pLTS or a pNet is the external action of the node shows the working status of it.
+The hole whose behavior is uncertain doesn't have an exact external presentation of action.
+We only give a variable to each hole and treat it as hole behavior to suppose working status of the hole.
+Here should have a constraint that this variable belongs to the sort of hole.
+In every case, the hole behaviors are unchanged, so we only make the combinations of subnets' open transitions.
+
+Algorithm 1 shows the combining algorithm for enumerating all the possible combinations of open transitions.
+The algorithm initializes an empty list $L_C$.
+Dealing with the list $TR$ containing several sets of open transitions from different subnets, the algorithm only chooses one of sets $L_{ot}$ and does combining on the rest part of $TR$ recursively then get a partial result of combining, $L'_C$.
+Since there could exist the case that the subnet is not working, a $null$ is added into the $L_{ot}$ to represent it.
+We get much more combinations after combining $ot$ from $L_{ot}$ with the partial result.
 \begin{algorithm}
@@
 
-\Require List $TR$ of result open transition lists from the subnets. 
-\Ensure All the possible combinations of open transitions.
-\State Initial an empty combination list $C$;
-\State Extract a list of open transitions $L$ from $TR$;
-\State Insert $null$ into $L$;
-\State Get the combinations $C'$ of the $TR$;
-\For{each $ot \in L$}
-	\For{each $tuple \in C'$}
-		\State Add $ot$ into $tuple$;
-		\State Add $tuple$ into $C$;
+\Require List $TR$ of result open transition sets from the subnets. 
+\Ensure The list of all the possible combinations of open transitions $L_C$.
+\State Initial an empty combination list $L_C$;
+\State Extract a list of open transitions $L_{ot}$ from $TR$;
+\State Insert $null$ into $L_{ot}$;
+\State Get the combinations $L'_C$ of the $TR$;
+\For{each $ot \in L_{ot}$}
+	\For{each $C' \in L'_C$}
+		\State Add $ot$ into $C'$ to get a new tuple $C$;
+		\State Add $C$ into $L_C$;
 	\EndFor
 \EndFor 
-\State \Return $C$;
+\State \Return $L_C$;
 
@@
 % 5. Return the result list of all the possible OTs.
+We now come to the matching using combinations from the previous step, together with hole behaviors and the result action, to match with the synchronization vectors.
+
+Every time we choose a synchronization vector for matching, we clone it and use the cloned one. We construct the predicates using the constraint declared before 
 \begin{algorithm}
@@
 \Require 
+The combination of subnets' open transitions $L_C$;
+The behaviors of the holes $B$;
+The set of synchronization vectors $SV$.
 \Ensure 
-
-\State \Return
+The list of all the possible open transitions generated $L_{ot}$.
+\State Initial an empty result list $L_{ot}$;
+\For{each $C \in L_C$}
+	\For{each $sv \in SV$}
+		\State Clone the $sv$, the result is denoted as $sv'$;
+		\State Generate the fresh result action v;
+		\State Combine $C, B, v$ as a new tuple $<C, B, v>$;
+		\For{each $e_1 \in <C, B, v> \&\& e_2 \in sv'$}
+			\If{$(e_1\ is\ null\ \&\&\ e_2\ is\ not\ null)\ ||\ (e_1\ is\ not\ null\ \&\&\ e_2\ is\ null)$} 
+			\State Skip;
+			\Else 
+			\State Generate the $Pred$;
+			\EndIf
+		\EndFor
+		\State Generate the result open transition $ot$ with $Pred$;
+		\State Add the $ot$ into $L_{ot}$;
+	\EndFor
+\EndFor 
+\State \Return $L_{ot}$;
 

### 2017-03-17 2017-Xudong-SMT/OpenPNets-SMT.tex
Merge description into section 5.
Fresh variable.
Predicate generation.

@@
 \newcommand{\sm}[1]{\mbox{\boldmath\small #1}}
+\usepackage{algorithm} 
+%\usepackage{algorithmicx} 
+\usepackage{algpseudocode}  
+\renewcommand{\algorithmicrequire}{\textbf{Input:}} 
+\renewcommand{\algorithmicensure}{\textbf{Output:}}
+\algnewcommand{\IfThenElse}[3]{\State \algorithmicif\ #1\ \algorithmicthen\ #2\ \algorithmicelse\ #3}% \IfThenElse{<if>}{<then>}{<else>}
 
@@
 
-\begin{algorithm}[Behavioural semantics of open pNets: Sketch]
+\begin{alg}[Behavioural semantics of open pNets: Sketch]
 This is a standard residual algorithm over a set of open-automaton
@@
 %unexplored set.
-\end{algorithm}
+\end{alg}
 
@@
 \TODO{Xudong: Detailed description of the implementation}
+
+\subsection{Fresh variable}
 \QIN{
-\\
-5.1 Generation of the Open Transition\\\\
-5.1.1 fresh variable\\\\
-The variable in each SV are considered local, so does the variable of an open transition such as its hole behavior and its result action.
-So we want rename them to make them unique, while we also hope them readable. The fresh variable has a confirmed format.
-As pNets has a tree-like structure, we give every node of the pNets a tree index.
-And give them some counters to count the current times the SV, Hole or subnet is used, and the number of possible OT generated.
-\\\\
-| format of fresh variable |\\\\
-5.1.2 predicate generation\\\\
-Combining, present all the possible working status of subnets. 
-[pseudocode]
-\\
-Mixing, match the elements of the combination to match the elements of the SV one by one to generate terms of a predicate.
-[pseudocode]
-\\\\
-5.1.3 assignment\\\\
+The variables in each synchronization vector are considered local, so does the variables of an open transition such as its hole behaviors and its result action.
+So we want rename the variables to make them unique on every occurrence of a vector.
+Similarly, the name given to the hole behaviors for each hole or the result action for each open transition must be distinct.
+At the same time, we also hope them still readable.
+Here we define the fresh variables, the variables renamed with a regular format by the function fresh().
+}
+
+\QIN{
+The fresh function is to generate a new name adding a suffix after the original name. The suffix contains three part combined by a colon. 
+}
+
+\begin{definition}[Fresh variable]\label{fresh-variable}
+The format of \emph{fresh variable} (renaming) is defined as:
+$$\emph{prefix : tree\ index\ :\ counter}$$
+\begin{itemize}
+   \item[$\bullet$] $prefix$ is a default internal name for the variable. So far the internal name can be  sva (SV action), ra (result action), hb (hole behavior).
+   \item[$\bullet$] $tree\ index$ is the index of the node in the tree-like structure of the pNet.
+   \item[$\bullet$] $counter$ is the current value of the corresponding counter.
+\end{itemize}
+\end{definition}
+
+\QIN{
+$Prefix$ avoids the confusion between variables from different structures with the same name by attaching the type of the structure.
+$Tree\ index$ is given to every node of the pNets to mention which node the variable belongs to as pNets has a tree-like structure.
+To each node, the tree index is always a number sequence of the tree index of its higher level and the index of the node in this level at the last.
+$A\ set\ of\ counters$ is used to count the current times the SV, Hole, subnet invoked, or the number of possible OT generated to provide an identity.
+}
+
+\subsection{Predicate generation}
+\QIN{
+The predicate of the open transition is a conjunction of two parts every time applying Tr2.
+One part composes the predicate from the subnets and the guard from transitions in sub-pLTS or synchronization vectors.
+The other part is the conjunction of equations generating during  synchronizing subnets' behaviors and synchronization vectors.
+Note that it is simple to collect required terms in the first part while in the second part it need to find out all the possible conjunction forms.
+We present here a algorithm divided in two step.
+Combining enumerates all the possible combinations of the working status.
+Matching synchronizes the subnets according to synchronization vectors to generate possible predicates.
+}
+%Combining is to generate all the possible matchings of the subnets' OTs (open transitions). The result list of the matched tuples called *combination*.
+% 1. Initialize the result list of OT tuples.
+% 2. Get one list of OTs. It's same as get OTs of one subnet.
+% 3. Add *null* into the list, it means this subnet does not work this time.
+% 4. Combine the rest subnets' OTs. Get the combination of the rest OTs.
+% 5. If there are OTs of the chosen list not be chosen, choose one OT.
+%      1. If there are tuples of the combination not be chosen, choose one tuple.
+%          1. Add the chosen OT into the tuple.
+%          2. Add the tuple into the result list, then do the recursion.
+% 6. Return the result list.
+\paragraph{Combining}
+\QIN{
+We first conduct combining.
+To each subnet, we enumerate all the possible cases of its working status.
+The result action of a pLTS or a pNet is the external action of the node shows the working status of it.
+The hole whose behavior is uncertain doesn't have an exact external presentation of action.
+We only give a variable to each hole and treat it as hole behavior to suppose working status of the hole.
+Here should have a constraint that this variable belongs to the sort of hole.
+In every case, the hole behaviors are unchanged, so we only make the combinations of subnets' open transitions.
+}
+
+\QIN{
+Algorithm 1 shows the combining algorithm for enumerating all the possible combinations of open transitions.
+The algorithm initializes an empty list $L_C$.
+Dealing with the list $TR$ containing several sets of open transitions from different subnets, the algorithm only chooses one of sets $L_{ot}$ and does combining on the rest part of $TR$ recursively then get a partial result of combining, $L'_C$.
+Since there could exist the case that the subnet is not working, a $null$ is added into the $L_{ot}$ to represent it.
+We get much more combinations after combining $ot$ from $L_{ot}$ with the partial result.
+}
+
+\begin{algorithm}
+\caption{Combining}
+\begin{algorithmic}[1]
+
+\Require List $TR$ of result open transition sets from the subnets. 
+\Ensure The list of all the possible combinations of open transitions $L_C$.
+\State Initial an empty combination list $L_C$;
+\State Extract a list of open transitions $L_{ot}$ from $TR$;
+\State Insert $null$ into $L_{ot}$;
+\State Get the combinations $L'_C$ of the $TR$;
+\For{each $ot \in L_{ot}$}
+	\For{each $C' \in L'_C$}
+		\State Add $ot$ into $C'$ to get a new tuple $C$;
+		\State Add $C$ into $L_C$;
+	\EndFor
+\EndFor 
+\State \Return $L_C$;
+
+\end{algorithmic}  
+\end{algorithm}
+
+% Mixing is to match the combination of the subnets' open transitions, hole behaviors and result action with the SV (synchronization vector) to generate the possible predicates of the OT (open transition).
+At the same time, other parameters of the OT (global state, subnets' transitions, result action...) are also generated.
+Then the possible OTs of the pNet can be achieved.
+% 1. Initialize the combination through the method *combineOpenTransitions( )*.
+% 2. Initialize the result list.
+% 3. Get the number of subnets and holes. They are used to decide how many element of the SV should be matched with them.
+% 4. For all tuples of the combination.
+%      1. Invoke the *clone( )* method to generate the fresh SV.
+%      2.
+Match the elements of the tuple with the elements of the SV.
+If there is a *null* matched with a *not null* action, filter this matching.
+Add the result expression and the predicate of the subnets into the predicate.
+Generate the target global state correspondingly.
+%      3. Match the hole behaviors with the elements of the SV. The hole behavior could be *null*. Add the result expression into the predicate.
+%      4. Match the result action with the result action of SV. Add the result expression into the predicate.
+%      5. Add the predicate into the OT. Store the OT in the result list.  
+% 5. Return the result list of all the possible OTs.
+\paragraph{Matching}
+\QIN{
+We now come to the matching using combinations from the previous step, together with hole behaviors and the result action, to match with the synchronization vectors. 
+}
+
+\QIN{
+Algorithm 2 shows the algorithm matches combination $L_C$, hole behaviors $B$ with synchronization vectors $SV$.
+Every time we choose a synchronization vector $sv$ from $SV$ for matching, we clone it and use the cloned one $sv'$.
+We use the definition declared before to construct all the possible predicates but the algorithm has not checked the correctness of these predicates.
+It needs a further refinement.
+}
+
+\QIN{
+In order to filter a part of mismatches, at any time an action $e_1$ matching with an element $e_2$ from synchronization vector, the pair $(e_1, e_2)$ must be checked: if both $e_1$ and $e_2$ are $null$ or $not\ null$, then it continues to generate a new term of predicate.
+Otherwise, it is intuitive that the working status coming from the subnet $e_1$ is different from what asked by the synchronization vector $e_2$, then this case is filtered.
+}
+\begin{algorithm}
+\caption{Matching}
+\begin{algorithmic}[1]
+
+\Require 
+The combination of subnets' open transitions $L_C$;
+The behaviors of the holes $B$;
+The set of synchronization vectors $SV$.
+\Ensure 
+The list of all the possible open transitions generated $L_{ot}$.
+\State Initial an empty result list $L_{ot}$;
+\For{each $C \in L_C$}
+	\For{each $sv \in SV$}
+		\State Clone the $sv$, the result is denoted as $sv'$;
+		\State Generate the fresh result action v;
+		\State Combine $C, B, v$ as a new tuple $<C, B, v>$;
+		\For{each $e_1 \in <C, B, v> \&\& e_2 \in sv'$}
+			\If{$(e_1\ is\ null\ \&\&\ e_2\ is\ not\ null)\ ||\ (e_1\ is\ not\ null\ \&\&\ e_2\ is\ null)$} 
+			\State Skip;
+			\Else 
+			\State Generate the term of predicate $t$;
+			\State Add $t$ into the $Pred$;
+			\EndIf
+		\EndFor
+		\State Generate the result open transition $ot$ with $Pred$;
+		\State Add the $ot$ into $L_{ot}$;
+	\EndFor
+\EndFor 
+\State \Return $L_{ot}$;
+
+\end{algorithmic} 
+\end{algorithm}
+
+\subsection{assignment}
 Management of state variables.\\
 Translating assignments into predicate terms.\\\\
-5.2 Pruning the unsatisfiable results\\\\
+
+\subsection{Pruning the unsatisfiable results}
 Interaction with Z3: pNets module ---input--> Z3 module [JAVA API]\\\\
-5.2.1 presentation\\\\
-5.2.2 checking satisfiability\\\\
+\paragraph{translation of presentation}
+\paragraph{checking satisfiability}
 After we get the result OTs, for each result OT, declare the variables and assertions in the Java API. Conduct checking method and get the result.\\
-}
+
 \ERIC{
@@
 
+\begin{figure}[t]
+  \includegraphics[width=\linewidth]{XFIG/CCSresult}
+  \caption{The open automaton of the CCS formula a.P||b.Q}  \label{schema:ccs-result}
+\end{figure}
+
 \bibliographystyle{lncs/splncs}

### 2017-03-17 2017-Xudong-SMT/OpenPNets-SMT.tex
Added todos for the next week

@@
 \section{Running Examples}
+Several publications \cite{PDP2015,FORTE2016} already have introduced
+many examples of pNets, encoding
+operators of various classical process algebras, or more complex
+synchronisation structures in distributed or parallel languages.
+In this section, we use two process expressions, respectively from CCS
+and from Lotos, to illustrate different features of pNets. They will
+serve as running examples in the whole paper.
+
 \TODO{Graph of two examples: CCS a.P||b.Q [DONE] and LOTOS (P>>Q)>>R}
@@
 
-\QIN{There are several former papers already have illustrated many examples in closed pNets show that pNets can properly simulate the original construct.
-In this section, we encode the operators from other algebras into the pNets present the feature of the open pNet.
-They will be the running examples in the whole paper.
-}
+\TODO{Xudong: correction of the 2 figures (CCS and LOTOS). Then Eric will write / rewrite the explanation text}
 
@@
 \subsection{Presentation of algebra}
+\TODO{Eric: write an introductory paragraph}
+
 \QIN{Before the encoding, the presentation of the pNet should be given first. We can divide the presentation into two parts:}
@@
 
-2d)
-\ERIC{Optionally, simplify the predicate by eliminating the unnecessary intermediate variables, that were produced as fresh local variables of synchronisation vectors, and fresh result variables of intermediate OTs.
-In the resulting predicate the only significant variables are :\\
-- the input variables of pLTS transitions\\
-- the actions of holes\\
-- the result action at toplevel.}
-
 For each open-transition,  add the transition in the outgoing transitions of
@@
 
-\TODO{Xudong: Detailed description of the implementation}
+\TODO{Xudong: Missing a general summary before going into details. You
+  can get inspiration from the following (reasonnable level of
+  abstraction):}
+\ERIC{
+=> Context = use the existing software architecture from VCE (ref to \cite{FASE} paper)\\
+=> Current prototype: programatic creation of pNet objects, through the pNet API in VCE. On the middle term, this should be compiled from some language or graphical formalism.\\
+=> Open transitions are computed as a direct implementation of the algorithm above.
+Steps 2a-2b are merged: at each pNet node, after application of rule Tr2, the resulting OT is built from the premisses, without explicitely constructing the deduction tree.
+\\
+=> Variable names are generated for all ``fresh'' and ``clone''
+operations, using structured variable names ensuring uniqueness of
+fresh names, but also reasonable readability of these names for
+debugging purposes.\\
+=> Assignements\\
+=> Satisfiability check is done only at toplevel of the deduction tree construction.
+An alternative would be to submit the satisfiability check to the SMT solver at each level of the tree construction, potentialy reducing the overall number of combinations.
+But submission to the SMT engine is costly, and more complexity analysis is required before deciding if this would be worthwhile.\\
+}
 
@@
 
-\ERIC{
-=> Context VCE, ref to FASE paper\\
-=> Current prototype: programatic creation of pNet objects, through the pNet API in VCE. On the middle term, this should be compiled from some language or graphical formalism.\\
-=> Open transitions are computed as a direct implementation of the algorithm above.
-Steps 2a-2b are merged: at each pNet node, after application of rule Tr2, the resulting OT is built from the premisses, without explicitely constructing the deduction tree.
-\\
-=> Variable names are generated for all ``fresh'' and ``clone''
-operations, using structured variable names ensuring uniqueness of
-fresh names, but also reasonable readability of these names for
-debugging purposes.\\
-=> Assignements\\
-=> Satisfiability check is done only at toplevel of the deduction tree construction.
-An alternative would be to submit the satisfiability check to the SMT solver at each level of the tree construction, potentialy reducing the overall number of combinations.
-But submission to the SMT engine is costly, and more complexity analysis is required before deciding if this would be worthwhile.\\
-=> Simplification is not yet implemented. It is not strictly required for the Open Automaton construction, but it will be critical later for predicate comparison in the bisimulation algorithm.}
-
 \TODO{
@@
 \label{section:conclusion}
+
+\TODO{Conclusion: what you have accomplished, clearly state your
+  contributions, and what is delivered at the end of your internship
+  work}
+
+\TODO{Discussion: next steps: 1) what is left as open questions on the
+  algorithm itself, what you have learned (is Z3 useful and efficient,
+  is it the right tool ?). 2) next important goal is bisimulation
+  checking, what is neded for that (formalize the algo, define and
+  implement simplification)}
+
+=> Simplification is not yet implemented. It is not strictly required
+for the Open Automaton construction, but it will be critical later for
+predicate comparison in the bisimulation algorithm.
+
+\ERIC{Optionally, simplify the predicate by eliminating the unnecessary intermediate variables, that were produced as fresh local variables of synchronisation vectors, and fresh result variables of intermediate OTs.
+In the resulting predicate the only significant variables are :\\
+- the input variables of pLTS transitions\\
+- the actions of holes\\
+- the result action at toplevel.}
 

### 2017-03-20 2017-Xudong-SMT/OpenPNets-SMT.tex
Update figure
CCS and LOTOS example figure in section 2.
Adjust the size and font.
Add the introduction for section 5
Add the introduction for section 5.

@@
 
-\begin{minipage}{6cm}
+\begin{minipage}{7cm}
   \includegraphics[width=\linewidth]{XFIG/CCS1}
@@
 \hspace{2mm}
-\begin{minipage}{6cm}
-  \includegraphics[width=\linewidth]{XFIG/Enable1}
+\begin{minipage}{5cm}
+  \includegraphics[width=\linewidth]{XFIG/Enable1.eps}
   \\[1.3ex]
-  \includegraphics[width=\linewidth]{XFIG/Enable2}
+  \includegraphics[width=\linewidth]{XFIG/Enable2.eps}
   \caption{Two pNet encodings for  Enable }  \label{schema:enable-pnets}
@@
 \section{Implementation}
+\QIN{
+VerCors platform uses pNet as the intermediate language for some language or graphical formalism to be translated into both input for a checker and for generating code automatically to ease the specification from non-expert users\cite{FASE}, compiling it from those language or graphical formalism in the pNet API.
+We compute the open automaton of an open pNet also in that pNet API directly implementing the sketch showed before.
+However, we made some modification, merging the step 2a-2b and applying Tr2 with the premisses from subnets to generate open transitions, application of Tr1 is still conducted in a simple way.
+At same time, we apply the fresh function to rename all the variable to make them unique and readable.
+Besides that, we also have a management of assignments throughout the whole computation.
+Satisfiability check is done only at top level of the deduction tree construction.
+An alternative would be to submit the satisfiability check to the SMT solver at each level of the tree construction, potentially reducing the overall number of combinations.
+But the submission to the SMT engine is costly, and more complexity analysis is required before deciding if this would be worthwhile.
+}
 
 \TODO{Xudong: Missing a general summary before going into details. You
-  can get inspiration from the following (reasonnable level of
+  can get inspiration from the following (reasonable level of
   abstraction):}
+
 \ERIC{
@@
 => Open transitions are computed as a direct implementation of the algorithm above.
-Steps 2a-2b are merged: at each pNet node, after application of rule Tr2, the resulting OT is built from the premisses, without explicitely constructing the deduction tree.
+Steps 2a-2b are merged: at each pNet node, after application of rule Tr2, the resulting OT is built from the premisses, without explicitly constructing the deduction tree.
 \\
@@
 debugging purposes.\\
-=> Assignements\\
-=> Satisfiability check is done only at toplevel of the deduction tree construction.
-An alternative would be to submit the satisfiability check to the SMT solver at each level of the tree construction, potentialy reducing the overall number of combinations.
+=> Assignments\\
+=> Satisfiability check is done only at top level of the deduction tree construction.
+An alternative would be to submit the satisfiability check to the SMT solver at each level of the tree construction, potentially reducing the overall number of combinations.
 But submission to the SMT engine is costly, and more complexity analysis is required before deciding if this would be worthwhile.\\

### 2017-03-20 2017-Xudong-SMT/OpenPNets-SMT.tex
running examples section

@@
 
-\TODO{Graph of two examples: CCS a.P||b.Q [DONE] and LOTOS (P>>Q)>>R}
-
-\TODO{Description of two examples: CCS a.P||b.Q [DONE] and LOTOS (P>>Q)>>R}
-
-\TODO{Xudong: correction of the 2 figures (CCS and LOTOS). Then Eric will write / rewrite the explanation text}
-
 \subsection{Operators from Classical Process Algebra}
-\QIN{First example we choose is a formula $a.P||b.Q$, composing the prefix operator and parallel operator of CCS. 
-In Fig. 1, we show the encoding of this CCS formula. The pNet has a tree-like structure. }
-
-\QIN{The root node of the tree PN1 is the top level of the pNet structure.
-It acts as the parallel operator.
-There are two subnodes, also called subnets, noted PN2 and PN3.
-Their behaviors are synchronized in their parent PN1 according to a set of synchronization vectors, synchronizing input and output action from these two subnets to give out a silent action $\tau$ or just making the action become visible on this level when one of subnets is not working.
-}
-
-\QIN{Its subnets act as the prefix operator, so these pNets have a same structure.
-There is a pLTS and a hole in each pNet node.
-The pLTS encoding the controller of the pNet.
-Collaborating with the synchronization vectors, the controller manages the specific behavior of the pNet.
-Such as in the pLTS C1, the only action start from the initial state is $a$ and there is a synchronization vector transmits it to the outside, it makes the first action always be $a$.
-A guard is added as a constraint into its notation in that we want this vector to only apply to the first action of C1.
-And another synchronization vector keeps the following actions come from the process $P$.
-The action of the process $P$ is uncertain here, so the hole is used as a process parameter of the pNet to present the behavior of the process $P$.
-that is what shows the open property.}
+
+\begin{figure}[h]
+  \centerline{\includegraphics[width=9cm]{XFIG/CCS1}}
+  \caption{The pNet encodings for CCS formula}  \label{schema:ccs-pnets}
+\end{figure}
+
+First example we choose is a formula $a.P||b.Q$, composing prefix and
+parallel operators of value-passing CCS, and containing two process
+variables (holes) P and Q. In Fig. 1, we show the encoding of this CCS
+formula. The pNet has a tree-like structure.
+
+The root node of the tree PN1 is the top level of the pNet
+  structure. It acts as the parallel operator. There are two subnets,
+  noted PN2 and PN3, each representing one of the prefix
+  sub-expression. Their behaviors are synchronized in their parent PN1
+  according to a set of synchronization vectors, synchronizing input
+  and output action from these two subnets to give out a silent action
+  $\tau$ or just making the action become visible on the top level when
+  one of the subnets is working alone. The vector syntax is typically
+  ``<act, \_ > -> act'', in which ``\_'' means that the corresponding
+  subnet is not involved in this synchronisation.
+  \TODO{The vectors for communication are wrong, we cannot use ?ch(v)
+    and !ch(v), see the PDP'15 and Forte'16 papers. }
+  Remark that these 4
+  synchronisation vectors correspond faithfully to the usual SOS
+  rules of CCS operational semantics.
+
+  Each of the subnets act as one of the prefix operator.
+In each of them there is a parameterised labelled transition system
+(pLTS) and a hole. The pLTS is a controller managing the
+changes of state of the pNet; consider C1, from its initial state the
+only possible transition performs the action variable $a$; once in
+state 1, the controler can perform (infinitely often) action $l$ that
+is a constant action local to C1 (that must be different from any
+other actino of the whole system). In the node PN2, there are 2
+synchronisation vectors, the first one transmits to the upper level the
+action $a$ (and thanks to C1, will only be activated one time); the
+second one transmit any action of the hole P, but only when C1 can
+perform $l$.
+
+It should be easy to see that this pNet system encodes properly the
+behavioural semantics of the corresponding CCS expression. Remarkk
+that it is built in a systematic structural way, one pNet node
+encoding each CCS operator. And it is parameterised both at the level
+of actions variables (occuring within the controllers and the synchronisation
+vectors), and at the level of process parameters 
+(holes).
 
 \subsection{Open pNet with Assignments in Leaves}
-
-\begin{figure}[t]
-
-\begin{minipage}{7cm}
-  \includegraphics[width=\linewidth]{XFIG/CCS1}
-  \caption{The pNet encodings for CCS formula}  \label{schema:ccs-pnets}
-\end{minipage}
-\hspace{2mm}
-\begin{minipage}{5cm}
-  \includegraphics[width=\linewidth]{XFIG/Enable1.eps}
-  \\[1.3ex]
-  \includegraphics[width=\linewidth]{XFIG/Enable2.eps}
-  \caption{Two pNet encodings for  Enable }  \label{schema:enable-pnets}
-\end{minipage}
+\begin{figure}[h]
+
+  \includegraphics[width=6cm]{XFIG/Enable1.eps}
+%  \hspace{0.5cm}
+  \includegraphics[width=6cm]{XFIG/Enable2.eps}
+  \caption{Two pNet encodings for the Lotos Enable operator P>>Q }  \label{schema:enable-pnets}
 
 \end{figure}
+
+In the second running example, we want to illustrate the use of local
+variables in the controller pLTSs. This example is based on the Enable
+operator of the LOTOS language. For the readers not familiar with
+Lotos, the pNet encodingss here should be sufficient to understand the
+Enable operator semantics.
+
+In fact we give two encodings of this operator: the first one is
+``state oriented'', in the sense that the controler has two states,
+indicating where the control point is in the P>>Q process expression,
+either in P or in Q. The transition between these occurs when process
+P performs a $\delta(x)$ action, transfering the control to Q, and
+sending a value $x$ at the same time. Process Q must be ready to
+``accept'' this value through an $acc(x)$ action. The controler C1,
+and the 3 synchronisation vectors of the Enable1 pNet should be easy
+to understand. Note 
+that the first vector, transmitting an action $a1$ of P, can only
+occur if $a1$ is not a $\delta$.
+
+The second encoding is ``data oriented'', meaning that the state of
+the node controller is encoded in the value of the pLTS state
+variable(s). Here we have a single state variable $s_0$, initialised
+as $0$. Its value is ``0'' when the control is on P, and ``1'' when the
+control is on Q. The transitions in the pLTS have the more general
+syntax: ``<action-expr> [guard] \{sequence of assignments\}''. Guards
+and assignments can only use the values of variables of their source
+state and values from input variables in the action expression; and a
+transition can only assign variables of its target state. 
+The second vector of the node ``Enable2'' also shows a
+$\underline{\delta(y_2)}$ result action, where the underlined action
+stands for an internal (already synchronised) action, that cannot be
+further synchronised at upper levels. This is a straighforward
+generalisation of the notion of internal actions, that will be
+convenient for observing internal events during model-checking.
 

### 2017-03-21 2017-Xudong-SMT/OpenPNets-SMT.tex
completed running exemples, and presentation of algebra

@@
   - open pNets to represent operators and program skeletons (ref to
-  \cite{PDP2015})\\
+  \cite{HMZ:PDP15})\\
   - compute semantics in term of open transitions\\
@@
 \section{Running Examples}
-Several publications \cite{PDP2015,FORTE2016} already have introduced
+Several publications \cite{HMZ:PDP15,henrio:Forte2016} already have introduced
 many examples of pNets, encoding
@@
   \TODO{The vectors for communication are wrong, we cannot use ?ch(v)
-    and !ch(v), see the PDP'15 and Forte'16 papers. }
+    and !ch(v), the action algebra has changed since PDP'2015, now you
+    must remove the ``?'' and ``!'' from the vectors. }
   Remark that these 4
@@
 \subsection{Presentation of algebra}
-\TODO{Eric: write an introductory paragraph}
-
-\QIN{Before the encoding, the presentation of the pNet should be given first. We can divide the presentation into two parts:}
+One of the important goal of the Open pNet framework is to provide us
+with a model able to express the semantics of many different algebras
+or languages. In particular, as we have seen in section
+\ref{section:pnets}, the \emph{term algebra} used to express the
+action expressions and the data in their parameters is left open in
+the pNet formalisation.
+
+So, for a given language, we now need to specify its data and action
+domains, giving them an abstract syntax (sorts, constructors, operators,
+and predicates). We call this a \emph{Presentation}.
+We also define a concrete syntax, that will be used for
+pretty-printing, but also for translating the presentation, and the
+predicates, into Z3 syntax.
+
+An algebra presentation contains:
 \begin{itemize}
-	\item Sorts: Constants sets of the algebra, types of the data and actions.
-	\item Operators: Operators comes from other algebras,  constructors for the parameterized actions.
+	\item Sorts: Constants sets of the algebra, types of the data
+          and actions. 
+	\item Operators: Operators comes from other algebras \TODO{why
+          others ? there can be action constructors also}
+          constructors for the parameterized actions.
+        \item Constants: The satifiability solver need to know which
+          actions in the pLTS behaviours are constants (like the $l$,
+          $r$ local actions of the controlers in the CCS example). So
+          for a given pNet system, the Action sort will include all
+          these constants.
 \end{itemize}
@@
 \paragraph{Sorts}
-\QIN{Ownership of the variables and constants in a pNet acting as actions or data is probably various.
-Sorts are represented by their name.
-The sort of actions is built by the constant actions.
-For example, let $CCSAct$ be the only set of actions of the CCS running example.
-Obviously, $CCSAct$ contains constant actions $l$, $r$ in the pLTSs.
-Sorts here act as sets of actions for pNet, pLTS or holes.
-Intuitively, Sorts of data and actions are completely independent.
-Sorts of the data like a type of them could be integer, boolean or a customized type.
-Sorts for integer and boolean are implicitly declared.}
+Ownership of the variables and constants in a pNet acting as actions
+or data is probably various. Sorts are represented by their name. The
+sort of actions is built by the constant actions. Sorts here act as
+sets of actions for pNet, pLTS or 
+holes. There \emph{must} be one sort for actions, and eventually
+several others for the types of data parameters. Sorts for integer
+and boolean are implicitly declared.
 
 \paragraph{Operators}
-\QIN{Usually we need introduce the expressions from other algebra when encoding the algebra into pNets.
-So that is needed to know about the input and output of the operators used in the expressions from those algebra.
-The input and output should belong to the sorts on the pNet.
-When there are $k$ sorts in this pNet, the structure of a $n$-ary operator is vector as $< Sort_{i_1}, ...
-, Sort_{i_n} > \rightarrow Sort_j , i_1 , ...
-, i_n, j \in [0..k] $.}
-
-\paragraph{Extension of other algebras}
-\QIN{Variable, constant are treated as a kind of expression together with the expression using operator.
-Operators can be categorized into unary operator, binary operator and N-ary operator, that make it possible to present operator from other algebras.
-In Fig .6, we show the Expression class we improved to enable user to extend other algebras in the pNet.
-There are classes implementing three kinds of expression extend the original  Expression class.
-From these three classes, more classes are extended using the operators coming from other algebra such as CCS and LOTOS}
+We need introduce operators for building expressions, of both action
+and data sorts, when encoding the 
+algebra into pNets. So that is needed to know about the input and
+output of the operators used in the expressions from those
+algebra. The input and output should belong to the sorts on the
+pNet. When there are $k$ sorts in this pNet, the structure of a
+$n$-ary operator is vector as $< Sort_{i_1}, ... , Sort_{i_n} >
+\rightarrow Sort_j , i_1 , ... , i_n, j \in [0..k] $.
+\TODO{ I do not understand this}
+
+\paragraph{Implementation of the expressions meta-model}
+The VerCors platform uses ECORE and EMF to define the structure of
+both pNets and actions algebras. There exists a predefined set of
+action and data expressions classes, including boolean, integer and
+action expressions, with predefined variables, literal (constants),
+and operators. Operators can be categorized into unary, binary and
+N-ary operators.
+The original version of VerCors did not allow to extend these classes,
+we have modified its architecture so that a user can extend them,
+defining more elements for his specific algebra.
+
+In Fig~\ref{schema:expression-pnets}, we show the Expression class we
+improved, including extensions for CCS and LOTOS.
 
@@
 \end{figure}
+
+\TODO{give an example of user-defined sorts/operators, and tell that
+  you will give it's translation into Z3 in section 5.4}
 
@@
 \QIN{
-VerCors platform uses pNet as the intermediate language for some language or graphical formalism to be translated into both input for a checker and for generating code automatically to ease the specification from non-expert users\cite{FASE}, compiling it from those language or graphical formalism in the pNet API.
-We compute the open automaton of an open pNet also in that pNet API directly implementing the sketch showed before.
-However, we made some modification, merging the step 2a-2b and applying Tr2 with the premisses from subnets to generate open transitions, application of Tr1 is still conducted in a simple way.
-At same time, we apply the fresh function to rename all the variable to make them unique and readable.
-Besides that, we also have a management of assignments throughout the whole computation.
-Satisfiability check is done only at top level of the deduction tree construction.
-An alternative would be to submit the satisfiability check to the SMT solver at each level of the tree construction, potentially reducing the overall number of combinations.
-But the submission to the SMT engine is costly, and more complexity analysis is required before deciding if this would be worthwhile.
+VerCors platform uses pNet as the intermediate language for some
+language or graphical formalism to be translated into both input for a
+checker and for generating code automatically to ease the
+specification from non-expert users\cite{HKM-FASE16}, compiling it
+from those language or graphical formalism in the pNet API. We compute
+the open automaton of an open pNet also in that pNet API directly
+implementing the sketch showed before. However, we made some
+modification, merging the step 2a-2b and applying Tr2 with the
+premisses from subnets to generate open transitions, application of
+Tr1 is still conducted in a simple way. At same time, we apply the
+fresh function to rename all the variable to make them unique and
+readable. Besides that, we also have a management of assignments
+throughout the whole computation. Satisfiability check is done only at
+top level of the deduction tree construction. An alternative would be
+to submit the satisfiability check to the SMT solver at each level of
+the tree construction, potentially reducing the overall number of
+combinations. But the submission to the SMT engine is costly, and more
+complexity analysis is required before deciding if this would be
+worthwhile. 
 }
@@
 \ERIC{
-=> Context = use the existing software architecture from VCE (ref to \cite{FASE} paper)\\
+=> Context = use the existing software architecture from VCE (ref to \cite{HKM-FASE16} paper)\\
 => Current prototype: programatic creation of pNet objects, through the pNet API in VCE. On the middle term, this should be compiled from some language or graphical formalism.\\

### 2017-03-21 2017-Xudong-SMT/OpenPNets-SMT.tex
Add more content in section 5
State var in section 3.
Tr1 and Tr2 changes.

@@
 		x_j\!\in\!\vars(s')$. %,  and $s= s'\Rightarrow J=\emptyset$. 
+\item[$\bullet$]
+\QIN{
+The $x_j$ here is called the $state\ variable$ of state $s'$.
+$State\ variables$ can only be modified by the assignment in the transition targets to its owner state.
+The global state variable of a pLTS is the variable $x$ satisfying $\forall s\!\in\!
+S .\, x\!\in\!
+\vars(s)$.
+}
 
@@
 
+The semantic of the open pNets is already defined as an open automaton in \cite{FORTE16} using open transitions to present the transitions of its global states.
 \begin{definition}[Operational semantics of open pNets]
@@
     { s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
-					J}\rangle} s'\in \to  }
+          J}\rangle} s'\in \to  \\
+      {\tt fresh}(v) \\
+      Pred = ~e_b \land (\alpha = v)
+    }
     { p = \mylangle  S,s_0, \to \myrangle
@@
       {\{s \xrightarrow{\alpha}_p s'\} ,\emptyset ,
-			e_b,\left\{x_j\gets e_j\right\}^{j\in J}}
-			{\ostate{s} \xrightarrow{\alpha} \ostate{s'}}
+      Pred,\left\{x_j\gets e_j\right\}^{j\in J}}
+      {\ostate{s} \xrightarrow{v} \ostate{s'}}
     }
@@
     {k\!\in\! K \\ SV\!\!= \!clone(SV_k) \!=\! \alpha_m^{m \in I_k\uplus J_k} \!\to\! 
-    \alpha'_k \\
+    \alpha'_k, G_k \\
       Leaves(p) \!=\! \pLTS_l^{l\in L} \\     
@@
       \Pred = \bigwedge_{m\in I_k}\!\! \Pred_m \land
-    	\Pred(SV,a_i^{i\in I_k},b_j^{j\in J_k},v)\\
+      \Pred(SV,v_m^{m\in I_k},b_j^{j\in J_k},v)\\
       \forall j\!\!\in\!\! J_k. {\tt 
@@
   \medskip  
-
 \end{definition}
+
 %
@@
 
-\subsection{assignment}
-Management of state variables.\\
-Translating assignments into predicate terms.\\\\
+\subsection{Management of assignments}
+\QIN{
+The pLTS contains some variables in its states, or just as global states of the pLTS, with several assignments.
+The algorithm composing assignments from subnets is different from the generation of predicates.
+When applying Tr1, we just keep the assignments in the Post of the open transition.
+And when it comes to Tr2, Post is the union of the assignments propagate from the subnets.
+The assignments provide value of the variables in predicates.
+There is usually not only one assignments for a variable and the assignment will lose when the algorithm computes other open transitions using other transitions in pLTS.
+The values of the variables are necessary for checking satisfiability of the open transitions together with predicates, miss of them may drop the unsatisfiable results.
+In order to avoid such mistakes, the algorithm manages the variables together with its all possible assignments.
+}
+
+\QIN{
+We use a list of triad $<v,\ S, \ AssignRH>$ for each pLTS to record the information of the state variables of the pLTS where $v$ is the state variable in pLTS, $S$ is its owner state and $AssignRH$ is a list of expressions over other variables in the right hand side of assignments of $v$.
+The $S$ can be $null$ in the record triad, but it means the variable is global in the pLTS belonging to all the states instead of meaning it belongs to nothing.
+So it should be noted that the changing of the value of the global state variable every time a transition is conducted.
+$AssignRH$ is the collection of all the possible expressions coming from the the right hand side of assignments.
+It keeps the information of the assignments for each state variable.
+We update the list of record triad every time Tr1 is applied, adding the right side of the assignments into corresponding expression lists.
+So the list keeps the all the assignments in the pLTS.
+Then we can track all the possible value of the variables when computing open transitions.
+The initial value of the state variable is also seemed as an assignment for that variable.
+We must give a initial value to the global state variable or there will be some problem in the start state.
+However, we sometimes don't give initial values to the state variables (except the global variables) as their initial values are decided by their first assignments, default values for them is hard to decide manually.
+}
 
@@
 Interaction with Z3: pNets module ---input--> Z3 module [JAVA API]\\\\
+\begin{figure}[t]
+  \includegraphics[width=\linewidth]{XFIG/Interaction}
+  \caption{The architecture of the interaction between pNet API and Z3}  \label{schema:interaction}
+\end{figure}
+
 \paragraph{translation of presentation}
+
+\paragraph{Translating assignments into predicate terms}
+\QIN{
+The assignments are also taken into account when checking the satisfiability of the open transitions as they present the value of the variables.
+In order to do that, we employs a translation from assignments into term of predicates.
+The assignments required to be translated are only those belong to the variables contain the in the start states of the open transitions.
+The assignments are represented as equations between the variables and the expressions on the right side of assignment.
+For the assignments of the same variable, we do not figure out which state is the precursor of current state, we keep all these possible equations instead, and generate the disjunction of these equations.
+The state could always move to the target state if there exists one of the values of its variable satisfies the guard.
+It won't matter the variable of the next state except that the right side expression contain its variables.
+This is a problem left to be solved in our future work.
+After that, for the assignments of the different variables, we generate a conjunction of them.
+This way we obtain a new term of the predicate involving assignments of the variables.
+}
+
 \paragraph{checking satisfiability}

### 2017-03-21 2017-Xudong-SMT/OpenPNets-SMT.tex
read and cleaned until page 13

@@
   $\tau$ or just making the action become visible on the top level when
-  one of the subnets is working alone. The vector syntax is typically
+  one of the subnets is working alone. The vector concrete syntax is typically
   ``<act, \_ > -> act'', in which ``\_'' means that the corresponding
   subnet is not involved in this synchronisation.
-  \TODO{The vectors for communication are wrong, we cannot use ?ch(v)
-    and !ch(v), the action algebra has changed since PDP'2015, now you
-    must remove the ``?'' and ``!'' from the vectors. }
+  There is also a difference with the usual CCS notation of
+  input/output actions: in the first vector, $ich$ and $ch$ are
+  corresponding input and output channels (see next section for a more
+  complete formalisation). 
   Remark that these 4
@@
 \item[$\bullet$]
-\QIN{
-The $x_j$ here is called the $state\ variable$ of state $s'$.
-$State\ variables$ can only be modified by the assignment in the transition targets to its owner state.
-The global state variable of a pLTS is the variable $x$ satisfying $\forall s\!\in\!
+The $x_j$ here are $state\ variables$ of state $s'$.
+$State\ variables$ can only be modified by the assignment in the transitions targetting its owner state.
+A global state variable of a pLTS is a variable $x$ satisfying $\forall s\!\in\!
 S .\, x\!\in\!
 \vars(s)$.
-}
 
@@
 
-\begin{figure}[t]
-\begin{minipage}{6.1cm}
-
-  \includegraphics[width=\linewidth]{XFIG/Enable1}
-  \\[1.3ex]
- \includegraphics[width=\linewidth]{XFIG/Enable2}
-  \caption{Two pNet encodings for  Enable }  \label{schema:enable-pnets}
-\end{minipage}
-  \hspace{2mm}
-\begin{minipage}{6cm}
-  \includegraphics[width=\linewidth]{XFIG/P-QR}
-  \caption{Composed pNet for ``P>>(Q>>R)''}  \label{schema:enable-composed}
-\end{minipage}
-
-\end{figure}
+%% \begin{figure}[t]
+%% \begin{minipage}{6.1cm}
+
+%%   \includegraphics[width=\linewidth]{XFIG/Enable1}
+%%   \\[1.3ex]
+%%  \includegraphics[width=\linewidth]{XFIG/Enable2}
+%%   \caption{Two pNet encodings for  Enable }  \label{schema:enable-pnets}
+%% \end{minipage}
+%%   \hspace{2mm}
+%% \begin{minipage}{6cm}
+%%   \includegraphics[width=\linewidth]{XFIG/P-QR}
+%%   \caption{Composed pNet for ``P>>(Q>>R)''}  \label{schema:enable-composed}
+%% \end{minipage}
+
+%% \end{figure}
 
@@
   \label{OT:enable-composed}
+  \TODO{ERIC: change for an OT of CCS example}
   The \texttt{EnableCompL} pNet of Fig. \ref{schema:enable-composed} has 2 controllers and 2 holes. One of its possible open-transition is:
@@
   In Fig. \ref{usingrules:OT2} we show the deduction tree used to construct and prove the 
-  open transition $OT_2$ of \texttt{EnableCompL} (see example page \pageref{OT:enable-composed}).
+  open transition $OT_2$ of \texttt{EnableCompL} (see example page
+  \pageref{OT:enable-composed}).
+  \TODO{Eric: change for a deduction tree of CCS expression}
   The rule uses TR1 for the $\delta$ transition of $C_3$, for the $l$ transition of $C_4$, then combines the result using the $a_4$ vector of the bottom pNet node, and the $\underline{\delta(x)}$ vector of the top node.
@@
           and actions. 
-	\item Operators: Operators comes from other algebras \TODO{why
-          others ? there can be action constructors also}
-          constructors for the parameterized actions.
+	\item Operators: Operators used to construct action
+          expressions (including their data parameters); they are
+          constructors of data and action sorts, but also predicates
+          over these objects.
         \item Constants: The satifiability solver need to know which
@@
 \rightarrow Sort_j , i_1 , ... , i_n, j \in [0..k] $.
-\TODO{ I do not understand this}
-
-\paragraph{Implementation of the expressions meta-model}
-The VerCors platform uses ECORE and EMF to define the structure of
+\TODO{ I do not understand this. As discussed today, I will wait till
+  you include an example of algebra presentation before rewriting the comment.}
+
+\paragraph{Implementation of the expression meta-model}
+The VerCors platform uses Ecore and EMF to define the structure of
 both pNets and actions algebras. There exists a predefined set of
@@
 build all possible deduction trees by application of the structural
-rules Tr1 and Tr2, using all \ERIC{applicable} combinations
+rules Tr1 and Tr2, using all applicable combinations
 of synchronisation vectors.
@@
 2c)
-\ERIC{The predicate is submitted to Z3 for checking satisfiability. If it is NOT stisfiable, the resulting OT is discarded. This will minimize the number of
-resulting transitions, and potentialy prune the search-space.}
+The predicate is submitted to Z3 for checking satisfiability. If it is
+NOT satisfiable, the resulting OT is discarded. This will minimize the
+number of 
+resulting transitions. Then a reachability check could potentialy
+prune the state space.
 
@@
 
+The proof can be found in \cite{FORTE16}.
+
 % Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in
@@
 \section{Implementation}
-\QIN{
-VerCors platform uses pNet as the intermediate language for some
-language or graphical formalism to be translated into both input for a
-checker and for generating code automatically to ease the
-specification from non-expert users\cite{HKM-FASE16}, compiling it
-from those language or graphical formalism in the pNet API. We compute
-the open automaton of an open pNet also in that pNet API directly
+The VerCors platform uses (closed) pNets as the intermediate language
+for some high-level language or graphical formalism to be translated
+into both input for a 
+model-checker and for generating executable code automatically \cite{HKM-FASE16}.
+% to ease the
+% specification from non-expert users, compiling it
+%from those language or graphical formalism in the pNet API.
+
+In our prototype we start directly with open pNets expressed
+programmaticaly, using the pNet API (graphical editors may be added
+later). From these, we compute
+the open automaton of an open pNet by directly
 implementing the sketch showed before. However, we made some
-modification, merging the step 2a-2b and applying Tr2 with the
-premisses from subnets to generate open transitions, application of
-Tr1 is still conducted in a simple way. At same time, we apply the
-fresh function to rename all the variable to make them unique and
-readable. Besides that, we also have a management of assignments
-throughout the whole computation. Satisfiability check is done only at
-top level of the deduction tree construction. An alternative would be
+modifications due to implementation choices:
+\begin{itemize}
+  \item Steps 2a-2b are merged, applying Tr2 from the
+premisses OTs from subnets to generate open transitions without
+explicitely constructing the deduction tree.
+  \item We defined a general naming schema for implementing the fresh 
+and clone functions to rename all the variable to make them unique, but also
+readable enough for debugging purpose.
+  \item Besides that, we also have designed a management of state variables and
+    assignments throughout the whole computation.
+  \item Satisfiability check is done only at
+top level of the open-transition construction. An alternative would be
 to submit the satisfiability check to the SMT solver at each level of
-the tree construction, potentially reducing the overall number of
+the hierarchical OT construction, potentially reducing the overall number of
 combinations. But the submission to the SMT engine is costly, and more
@@
 worthwhile. 
-}
-
-\TODO{Xudong: Missing a general summary before going into details. You
-  can get inspiration from the following (reasonable level of
-  abstraction):}
-
-\ERIC{
-=> Context = use the existing software architecture from VCE (ref to \cite{HKM-FASE16} paper)\\
-=> Current prototype: programatic creation of pNet objects, through the pNet API in VCE. On the middle term, this should be compiled from some language or graphical formalism.\\
-=> Open transitions are computed as a direct implementation of the algorithm above.
-Steps 2a-2b are merged: at each pNet node, after application of rule Tr2, the resulting OT is built from the premisses, without explicitly constructing the deduction tree.
-\\
-=> Variable names are generated for all ``fresh'' and ``clone''
-operations, using structured variable names ensuring uniqueness of
-fresh names, but also reasonable readability of these names for
-debugging purposes.\\
-=> Assignments\\
-=> Satisfiability check is done only at top level of the deduction tree construction.
-An alternative would be to submit the satisfiability check to the SMT solver at each level of the tree construction, potentially reducing the overall number of combinations.
-But submission to the SMT engine is costly, and more complexity analysis is required before deciding if this would be worthwhile.\\
-}
-
-\subsection{Fresh variable}
-\QIN{
-The variables in each synchronization vector are considered local, so does the variables of an open transition such as its hole behaviors and its result action.
-So we want rename the variables to make them unique on every occurrence of a vector.
-Similarly, the name given to the hole behaviors for each hole or the result action for each open transition must be distinct.
-At the same time, we also hope them still readable.
-Here we define the fresh variables, the variables renamed with a regular format by the function fresh().
-}
-
-\QIN{
-The fresh function is to generate a new name adding a suffix after the original name. The suffix contains three part combined by a colon. 
-}
+\end{itemize}
+
+\subsection{Fresh variables}
+
+The variables in each synchronization vector are considered local, so
+does the variables of an open transition such as its hole behaviors
+and its result action. So we want rename the variables to make them
+unique on every occurrence of a vector. Similarly, the name given to
+the hole behaviors for each hole or the result action for each open
+transition must be distinct. At the same time, we also hope them still
+readable. Here we have defined a structure for the name of the fresh
+variables, the variables renamed with a regular format by the function
+fresh().
+
+More precisely, the fresh function generates a new name adding a
+suffix after the original name. The suffix contains three parts
+combined by a colon.
 
@@
 \end{definition}
+
+\TODO{Add the process and the vector ids ?}
 

### 2017-03-23 2017-Xudong-SMT/OpenPNets-SMT.tex
Add the introduction of pruning unsatifiability
In section 5, add some graphs, and TODO.
Also add a part of the result in conclusion.

@@
 \subsection{Pruning the unsatisfiable results}
-Interaction with Z3: pNets module ---input--> Z3 module [JAVA API]\\\\
+\QIN{
+We have used a brute-force method to generate all the possible open transitions in the open automaton.
+It obviously contains some of unsatisfiability in the open transitions.
+In Fig~\ref{schema:unsat-ot}, we show an unsatisfiable open transition from the result of the CCS running example.
+It presents the case that the top level transmits out the action from the PN2, formula $a.P$, as this time only PN2 is working and C1 is performing action $a$ when hole $P$ is also working.
+In this case, the second synchronization vector of PN2, transmitting the behavior from hole $P$ to the higher level, is used while it is obviously violate the guard of the vector.
+So we can easily find the contradiction between the generated predicate term $ra:152:1=l \!\land\!
+a=:ra:152:1$ and the guard composed into the predicate $a \neq l$.
+To get a correct open automaton of the pNet, such unsatisfiable open transitions need to be eliminated.
+We choose a SMT solver Z3 as the checker for the open transitions considering the predicates may contain the expression using uninterpreted functions declared by users.
+}
+\begin{figure}[t]
+$\begin{array}{@{}r@{}l@{}}
+%{s0---a-->s1},   {---:hb:15:2-->},   (:ra:15:2 = act:sva:1:3)/\(:ra:152:1 = l)/\(a = :ra:152:1)/\(l!= a)/\(:hb:15:2 = y:sva:15:2)/\(:ra:15:2 = y:sva:15:2)/\(y:sva:15:2 != l)/\(:ra:1:3 = act:sva:1:3)
+    ot  = &\openrule{\{0 \xrightarrow{a} 1\}, ~~\{\xrightarrow{:hb:15:2}\}, ~~:ra:15:2=act:sva:1:3 \\
+    \!\land\!:ra:152:1=l \!\land\! a=:ra:152:1 \!\land\! a \neq l \!\land\! :hb:15:2 = y:sva:15:2 \\
+    \!\land\! :ra:15:2 = y:sva:15:2  \!\land\! y:sva:15:2 \neq l \!\land\! :ra:1:3 = act:sva:1:3}
+    {\ostate{00} \xrightarrow{:ra:1:3} \ostate{10}}\\
+  \end{array}$
+\caption{One of the unsatisfiable open transitions in CCS running example)}  \label{schema:unsat-ot}
+\end{figure}
+
+%\begin{figure}[t]
+%  \includegraphics[width=\linewidth]{XFIG/SMTLIB1}
+%  \caption{The input of the Z3 solver in SMT-LIB language and the output result}  \label{schema:smt-lib}
+%\end{figure}
+
 \begin{figure}[t]
@@
 \end{figure}
+
+\paragraph{Interaction with Z3}
+\QIN{
+\TODO{1. example input of Z3 in SMT-LIB 2. software architecture.}
+}
 
@@
 
-\begin{figure}[t]
-  \includegraphics[width=\linewidth]{XFIG/CCSresult}
-  \caption{The open automaton of the CCS formula a.P||b.Q}  \label{schema:ccs-result}
+\begin{figure}[h]
+  \centerline{\includegraphics[width=7cm]{XFIG/CCSresult}}
+
+$\begin{array}{@{}r@{}l@{}}
+    ot_1  = &\openrule{\{0 \xrightarrow{a} 1, 0 \xrightarrow{b} 1\}, ~~a=ich(v_{11}) \!\land\! b=ch(v_{11}) \!\land\! a\neq l \!\land\! b\neq r\!\land\! v_1=\tau}
+    {\ostate{00} \xrightarrow{v_1} \ostate{11}}\\
+  \end{array}$
+
+  \begin{minipage}{6cm}
+$\begin{array}{@{}r@{}l@{}}
+    ot_3  = &\openrule{\{0 \xrightarrow{a} 1\}, ~~a\neq l \!\land\! v_3=a}
+    {\ostate{00} \xrightarrow{v_3} \ostate{10}}\\
+    ot_5  = &\openrule{\{0 \xrightarrow{b} 1\}, ~~b\neq r \!\land\! v_5=b}
+    {\ostate{10} \xrightarrow{v_5} \ostate{11}}\\
+  \end{array}$
+  \end{minipage}
+   \hspace{2mm}
+  \begin{minipage}{6cm}
+$\begin{array}{@{}r@{}l@{}}
+    ot_7  = &\openrule{\{1 \xrightarrow{l} 1\}, ~~\{\xrightarrow{hb_{17}}\}, ~~v_7=hb_{17}}
+    {\ostate{10} \xrightarrow{v_7} \ostate{10}}\\
+  \end{array}$
+  \end{minipage}
+
+$\begin{array}{@{}r@{}l@{}}
+    ot_9  = &\openrule{\{0 \xrightarrow{b} 1, 1 \xrightarrow{l} 1\}, ~~\{\xrightarrow{hb_{19}}\}, ~~b=ich(v_{19}) \!\land\! b\neq r \!\land\! hb_{19}= ch(v_9)\!\land\! v_9=\tau}
+    {\ostate{10} \xrightarrow{v_9} \ostate{11}}\\
+  \end{array}$
+
+$\begin{array}{@{}r@{}l@{}}
+    ot_{13}  = &\openrule{\{1 \xrightarrow{l} 1, 1 \xrightarrow{r} 1\}, ~~\{\xrightarrow{hb_{113}}, \xrightarrow{hb_{213}}\}, ~~hb_{113}= ich(v_{13}) \!\land\!
+hb_{213}= ch(v_{13}) \!\land\!
+v_{13}=\tau}
+    {\ostate{11} \xrightarrow{v_{13}} \ostate{11}}\\
+  \end{array}$
+
+$\begin{array}{@{}r@{}l@{}}
+    ot_{15}  = &\openrule{\{1 \xrightarrow{l} 1\}, ~~\{\xrightarrow{hb_{115}}\}, ~~v_{15}=hb_{115}}
+    {\ostate{11} \xrightarrow{v_{15}} \ostate{11}}\\
+  \end{array}$
+
+\caption{The open automaton of the CCS formula a.P||b.Q (a part of open transitions is shown)}  \label{schema:ccs-result}
 \end{figure}

### 2017-03-23 2017-Xudong-SMT/OpenPNets-SMT.tex
Add the description of interaction with Z3
In section 5, the description of input example and architecture. two graphs used.

@@
 
-%\begin{figure}[t]
-%  \includegraphics[width=\linewidth]{XFIG/SMTLIB1}
-%  \caption{The input of the Z3 solver in SMT-LIB language and the output result}  \label{schema:smt-lib}
-%\end{figure}
+\begin{figure}[t]
+  \centerline{\includegraphics[width=10cm]{XFIG/SMTLIB1}}
+  \caption{The input of the Z3 solver in SMT-LIB language and the output result}  \label{schema:smt-lib}
+\end{figure}
 
@@
 \paragraph{Interaction with Z3}
+\TODO{1. example input of Z3 in SMT-LIB.[DONE] 2. software architecture.[DONE]}
 \QIN{
-\TODO{1. example input of Z3 in SMT-LIB 2. software architecture.}
+We implement the dynamic interaction between the pNet API and Z3 solver through its JAVA API.
+But here we present the code in Z3 by SMT-LIB language instead of JAVA codes to make it easier to read.
+In Fig~\ref{schema:smt-lib}, we show the manual input of the unsatisfiable result before.
+Some $datatypes$ are declared to input the sorts of the CCS example, here we only declare one $datatypes$ named $Action$ to involve all the constant actions.
+The $Int$ and $Bool$ are already existed in Z3.
+Then we input the predicate of that open transition in two parts.
+The variables contained in the predicate are declared first, then the terms of predicate are inputed as $assertions$ one by one.
+In the output, "(not and)" shows Z3 have found out the contradiction in the predicate and the result "unsat" is just what we expected.
+}
+
+\QIN{
+We present the architecture of the interaction with Z3 in Fig~\ref{schema:interaction}.
+Both two parts need to be translated before submitting to the Z3.
+The $presentation$ of the pNet is declared at the beginning of the algorithm as the $sorts$ and the $operators$ will be used throughout the whole algorithm.
+It is translated into $datatypes$ and $functions$ then submitted to the Z3 at the same time.
+The predicate will be translated into $assertions$ before submitted to Z3 after the algorithm computing out all the possible open transitions, they act as intermediate results there.
+Together with the $datatypes$ and $functions$, the $assertions$ are used to check the satisfiability of the predicate in Z3.
 }
@@
 \paragraph{translation of presentation}
+\QIN{
+The $datatypes$ are declared according to the $sorts$ the users declared in the $presentation$.
+Although in Fig~\ref{schema:smt-lib} we have not declared $functions$, they will be required if there are new $operators$ declared in the $presentation$.
+If the return type of the functions is one of the $datatypes$, we add this $function$ when declare the $datatypes$, it present the reality that every action expression also belongs to a sort of pNet.
+}
+
+\paragraph{checking satisfiability}
+After we get the result OTs, for each result OT, declare the variables and assertions in the Java API. Conduct checking method and get the result.\\
 
@@
 
-\paragraph{checking satisfiability}
-After we get the result OTs, for each result OT, declare the variables and assertions in the Java API. Conduct checking method and get the result.\\
-
+\subsection{Result of the running example}
 \TODO{
@@
 }
-
-\section{Conclusion and Discussion}
-\label{section:conclusion}
-
-\TODO{Conclusion: what you have accomplished, clearly state your
-  contributions, and what is delivered at the end of your internship
-  work}
-
-\TODO{Discussion: next steps: 1) what is left as open questions on the
-  algorithm itself, what you have learned (is Z3 useful and efficient,
-  is it the right tool ?). 2) next important goal is bisimulation
-  checking, what is neded for that (formalize the algo, define and
-  implement simplification)}
-
-=> Simplification is not yet implemented. It is not strictly required
-for the Open Automaton construction, but it will be critical later for
-predicate comparison in the bisimulation algorithm.
-
-\ERIC{Optionally, simplify the predicate by eliminating the unnecessary intermediate variables, that were produced as fresh local variables of synchronisation vectors, and fresh result variables of intermediate OTs.
-In the resulting predicate the only significant variables are :\\
-- the input variables of pLTS transitions\\
-- the actions of holes\\
-- the result action at toplevel.}
 
@@
 
+\section{Conclusion and Discussion}
+\label{section:conclusion}
+
+\TODO{Conclusion: what you have accomplished, clearly state your
+  contributions, and what is delivered at the end of your internship
+  work}
+
+\TODO{Discussion: next steps: 1) what is left as open questions on the
+  algorithm itself, what you have learned (is Z3 useful and efficient,
+  is it the right tool ?). 2) next important goal is bisimulation
+  checking, what is neded for that (formalize the algo, define and
+  implement simplification)}
+
+=> Simplification is not yet implemented. It is not strictly required
+for the Open Automaton construction, but it will be critical later for
+predicate comparison in the bisimulation algorithm.
+
+\ERIC{Optionally, simplify the predicate by eliminating the unnecessary intermediate variables, that were produced as fresh local variables of synchronisation vectors, and fresh result variables of intermediate OTs.
+In the resulting predicate the only significant variables are :\\
+- the input variables of pLTS transitions\\
+- the actions of holes\\
+- the result action at toplevel.}
+
 \bibliographystyle{lncs/splncs}

### 2017-03-24 2017-Xudong-SMT/OpenPNets-SMT.tex
More content in "interaction with Z3"
Left - the transition of the predicates
     - the result analysis
     - the conclusion

@@
 The $datatypes$ are declared according to the $sorts$ the users declared in the $presentation$.
-Although in Fig~\ref{schema:smt-lib} we have not declared $functions$, they will be required if there are new $operators$ declared in the $presentation$.
-If the return type of the functions is one of the $datatypes$, we add this $function$ when declare the $datatypes$, it present the reality that every action expression also belongs to a sort of pNet.
-}
+If the return type of the $functions$ is one of the $datatypes$, we add this $function$ when declare the $datatypes$, it present the reality that every action expression also belongs to a sort of pNet.
+Although in Fig~\ref{schema:smt-lib} we have not declared $functions$, they should be exactly declared if there are new $operators$ declared in the $presentation$.
+The input type of the $function$ can be $Int$, $Bool$ or the $datatypes$ declared all determined by the construct of the  $operators$ in the presentation.
+For example, we define a new operator to present the equation between two actions in CCS example $\text{EQUAL}$ in the format likes:
+}
+\[< Action , Action > \rightarrow Bool .\]
+\QIN{
+It will be translated into the Z3 statement: 
+}
+\[(declare\text{-}fun\ \text{EQUAL}\ (Action\ Action)\ Bool) .\]
 
 \paragraph{checking satisfiability}
-After we get the result OTs, for each result OT, declare the variables and assertions in the Java API. Conduct checking method and get the result.\\
+\TODO{After we get the result OTs, for each result OT, declare the variables and assertions in the Java API. Conduct checking method and get the result.\\}
 

### 2017-03-24 2017-Xudong-SMT/OpenPNets-SMT.tex
ccs OTs

--- 2017-03-23 2017-Xudong-SMT/OpenPNets-SMT.tex
@@
 for more general mechanisms, like gate negociation in Lotos, or broadcast
-communications. Using our notations, value-passing actions \emph{\`a la} CCS would be
-encoded as $a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs (in which $v_i$ are 
-action terms containing no input variables). 
+communications.
+\ERIC{Formaly, value-passing actions \emph{\`a la} CCS, denoted as ``?ch(x)'' and ``!ch(exp)'' in our CCS running example, stand respectively for $CCSact(i(ch),?x)$ and $CCSact(ch,exp)$, where $ch$ is a variable denoting a channel name, $?x$ is an input variable denoting the data argument received as input on $ch$, and $exp$ some data expression (containing no input variables).
+}
 %For Lotos-style
@@
 \begin{example}\emph{An open-transition.}
-  \label{OT:enable-composed}
-  \TODO{ERIC: change for an OT of CCS example}
-  The \texttt{EnableCompL} pNet of Fig. \ref{schema:enable-composed} has 2 controllers and 2 holes. One of its possible open-transition is:
+  \label{OT:ccs-composed}
+%  \TODO{ERIC: change for an OT of CCS example}
+\ERIC{  The \texttt{CCS} pNet of Fig.
+\ref{schema:ccs-pnets} has 2 controllers and 2 holes.
+We show its full open Automaton in section \ref{section:full-result}, it has 16 open transitions.
+We detail 3 of them here:}
 
  \smallskip
- $  OT_2  = \openrule{
-                       0 \xrightarrow{\delta}_{C_3} 1 ~~
-                            0 \xrightarrow{l}_{C_4} 0  ~~                 
-                            \xrightarrow{\delta(x4)}_P ~~
-                            \xrightarrow{accept(x4)}_Q 
-                      }
-  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
-    {A1_0 \xrightarrow{\underline{\delta(x4)}} A1_1}
+ $  OT_1  = \openrule{
+                       0 \xrightarrow{a}_{C_1} 1 ~~
+                       0 \xrightarrow{b}_{C_2} 1  ~~
+                       \{\}               ~~
+                 [ a\neq l \land b\neq r \land a=?ch(v) \land b=!ch(v) ]              
+                      }
+     {\ostate{00} \xrightarrow{\underline{\tau}} \ostate{10}}$
+
+ $ OT_3  = \openrule{
+                       0 \xrightarrow{a}_{C_1} 1 ~~
+                       \{\}               ~~
+                 [ a\neq l  ]              
+                      }
+     {\ostate{10} \xrightarrow{a} \ostate{11}} $
+
+$  OT_{11}  = \openrule{
+                          1 \xrightarrow{l}_{C_1} 1 ~~
+                       0 \xrightarrow{b}_{C_2} 1 ~~
+                       \{ \xrightarrow{b_P}_{P} \}               ~~
+                 [ a\neq l \land b\neq r \land b_P=?ch(v) \land b=!ch(v) ]              
+                      }
+     {\ostate{10} \xrightarrow{\tau} \ostate{11}}
   $
 \end{example}
+\TODO{Eric: short comments}
 
@@
     open-transitions}
-  In Fig. \ref{usingrules:OT2} we show the deduction tree used to construct and prove the 
-  open transition $OT_2$ of \texttt{EnableCompL} (see example page
-  \pageref{OT:enable-composed}).
-  \TODO{Eric: change for a deduction tree of CCS expression}
-  The rule uses TR1 for the $\delta$ transition of $C_3$, for the $l$ transition of $C_4$, then combines the result using the $a_4$ vector of the bottom pNet node, and the $\underline{\delta(x)}$ vector of the top node.
+  In Fig. \ref{usingrules:OT11} we show the deduction tree used to construct and prove the 
+  open transition $OT_{11}$ of \texttt{CCS} (see example page
+  \pageref{OT:ccs-composed}).
+%  \TODO{Eric: change for a deduction tree of CCS expression}
+\ERIC{  The rule uses TR1 for the $l$ transition of $C_1$ and for the $b$ transition of $C_2$, uses an action $b_P$ of hole $P$, then combines the result using the second vector of the PN2 sub-pNet, and the third vector of the top node.
+This yield a final $\tau$ transition.
+The deduction tree in the figure shows how the predicate are generated in this process.
+}
 
@@
 \subsection{Result of the running example}
+\label{section:full-result}
 \TODO{

### 2017-03-24 2017-Xudong-SMT/OpenPNets-SMT.tex
Merge

@@
 communications.
-\ERIC{Formaly, value-passing actions \emph{\`a la} CCS, denoted as ``?ch(x)'' and ``!ch(exp)'' in our CCS running example, stand respectively for $CCSact(i(ch),?x)$ and $CCSact(ch,exp)$, where $ch$ is a variable denoting a channel name, $?x$ is an input variable denoting the data argument received as input on $ch$, and $exp$ some data expression (containing no input variables).
+\ERIC{Formally, value-passing actions \emph{\`a la} CCS, denoted as ``?ch(x)'' and ``!ch(exp)'' in our CCS running example, stand respectively for $CCSact(i(ch),?x)$ and $CCSact(ch,exp)$, where $ch$ is a variable denoting a channel name, $?x$ is an input variable denoting the data argument received as input on $ch$, and $exp$ some data expression (containing no input variables).
+In our example we will use the usual CCS syntax.
 }
@@
 
-The semantic of the open pNets is already defined as an open automaton in \cite{FORTE16} using open transitions to present the transitions of its global states.
+The semantic of the open pNets is already defined as an open automaton in \cite{henrio:Forte2016} using open transitions to present the transitions of its global states.
 \begin{definition}[Operational semantics of open pNets]
@@
 
-The proof can be found in \cite{FORTE16}.
+The proof can be found in \cite{henrio:Forte2016}.
 

### 2017-03-24 2017-Xudong-SMT/OpenPNets-SMT.tex
Dediction tree for CCS

@@
 %  \TODO{Eric: change for a deduction tree of CCS expression}
-\ERIC{  The rule uses TR1 for the $l$ transition of $C_1$ and for the $b$ transition of $C_2$, uses an action $b_P$ of hole $P$, then combines the result using the second vector of the PN2 sub-pNet, and the third vector of the top node.
-This yield a final $\tau$ transition.
-The deduction tree in the figure shows how the predicate are generated in this process.
+\ERIC{  The proof tree uses TR1 for the $l$ transition of $C_1$ and for the
+  $b$ transition of $C_2$, then uses an action $b_P$ of hole $P$, then
+  combines the results using the second vector of the PN2 sub-pNet, and
+  the third vector of the top node. This yields a final $\tau$
+  transition. The deduction tree in the figure shows how the
+  predicates are generated in this process. 
 }
@@
     {\inferrule
-        {0 \xrightarrow {\delta}_{C_3} 1}
-        {C_3
+      {
+          \inferrule
+              {1 \xrightarrow {l}_{C_1} 1}
+              {C_1
+                \models
+                \openrule
+                      {1 \xrightarrow{l}_{C_1} 1}
+                      {\ostate{1}\xrightarrow{1}\ostate{1}}
+              }
+        }
+        {\textrm{a:P}
           \models
             \openrule{
-              0 \xrightarrow {\delta}_{C_3} 1,\,
-              \{\xrightarrow{\delta(x_1)}_P\},\,
-              v_1=\delta(x_1)}
-                      {\ostate{0}\xrightarrow{v_1}\ostate{1}}
+              1 \xrightarrow {l}_{C_1} 1,\,
+              \{\xrightarrow{b_P}_P\},\, b_P\neq l}
+                      {\ostate{1}\xrightarrow{b_P}\ostate{1}}
         }\\
@@
         {
-%          \sm{fresh}{a_Q} \\
           \inferrule
-              {0 \xrightarrow{l}_{C_4} 0}
-              % {\ostate{0}\xrightarrow{l}\ostate{0}}
+              {0 \xrightarrow{b}_{C_2} 1}
               {C_4
                 \models
+                \openrule
+                      {0 \xrightarrow{b}_{C_2} 0,\, b\neq r}
+                      {\ostate{0}\xrightarrow{b}\ostate{1}}
+              }
+        }
+        {
+          \textrm{b:Q}\models
+              \openrule
+                  { 0 \xrightarrow {b}_{C_2} 1,\, \ b\neq r}
+                  {\ostate{0}\xrightarrow{b}\ostate{1}}
+        }   
+    }
+    {
+     \textrm{PN1}
+     \models
         \openrule{
-                      0 \xrightarrow l_{C_4} 0,\,
-                      \sm{Pred}_{C_4}}
-                      {\ostate{0}\xrightarrow{l}\ostate{0}}
-              }
-        }
-        {
-          \textrm{Q>>R}\models
-              \openrule
-                  { 0 \xrightarrow {l}_{C_4} 0,\,
-                    \{\xrightarrow{acc(x_2)}_Q\},\,
-                    \ v_2=acc(x_2)
-                  }
-                  {\ostate{0}\xrightarrow{v_2}\ostate{0}}
-        }   
-    }
-    {
-     \textrm{P>>(Q>>R)}
-     \models
-     \openrule
-         { 0 \xrightarrow{\delta}_{C_3} 1, \\ 0 \xrightarrow{l}_{C_4} 0,\\
-           \{\xrightarrow{\delta(x)}_P,\,\xrightarrow{acc(x)}_Q\}, \\
-            a_3=v_1 \wedge v=a_3 \wedge x_1=x_2
-           }
-         {\ostate{00} \xrightarrow{v} \ostate{10}}
+                       1 \xrightarrow{l}_{C_1} 1 ~~
+                       0 \xrightarrow{b}_{C_2} 1 ~~
+                       \{ \xrightarrow{b_P}_{P} \}               ~~
+                 [ a\neq l \land b\neq r \land b_P=?ch(v) \land b=!ch(v) ]              
+                      }
+     {\ostate{10} \xrightarrow{\tau} \ostate{11}}
       }\vspace{-4ex}
 \end{mathpar}
-  \caption{Proof of transition $OT_2$ (with interaction of processes $P$ and $Q$) for ``P>>(Q>>R)''}
+  \caption{Proof of  $OT_{11}$ (with interaction of processes $P$ and action $b$) for ``a.P||b.Q''}
   \label{usingrules:OT2}

### 2017-03-26 2017-Xudong-SMT/OpenPNets-SMT.tex
Finish Section 5 and Conclusion
The description of the checking method and the analysis of the result.
The notation for the hb is not comfirmed.
The conclusion.

@@
 
-\paragraph{translation of presentation}
+\paragraph{Translation of presentation}
 \QIN{
@@
 }
-\[(declare\text{-}fun\ \text{EQUAL}\ (Action\ Action)\ Bool) .\]
-
-\paragraph{checking satisfiability}
-\TODO{After we get the result OTs, for each result OT, declare the variables and assertions in the Java API. Conduct checking method and get the result.\\}
+\[\text{(declare-fun\ EQUAL\ (Action\ Action)\ Bool) .}\]
 
@@
 
+\paragraph{checking satisfiability}
+\TODO{After we get the result OTs, for each result OT, declare the variables and assertions in the Java API. Conduct checking method and get the result.[DONE]\\}
+\QIN{
+We check the satisfiability of open transitions on the top level of the pNet, treating these open transitions as the intermediate result of the algorithm.
+After we get the intermediate results of open transitions, we check them one by one.
+Here we declare the variables in the predicate first to make Z3 know all the parameters used for checking this time.
+The variable including the argument in the operators must has its sort as every pNet defines two default sorts $Int$, $Bool$ default and at least one sort for the actions.
+The variables can declared using the $datatypes$ declared in the format as:
+}
+\[\text{(declare-const\ a\ Action) .}\]
+
+\QIN{
+The predicate submitted to the Z3 contain the assignments as them become a part of predicate after our translation.
+Each term of the predicate is an assertion in Z3, as an example, in the former unsatisfiable result, the contradiction is occured in terms:
+}
+\[(:ra:152:1 = l) \land (a = :ra:152:1) \land (l \neq a) .\]
+\QIN{
+from which we generate following three assertion:
+}
+\[\text{(assert\ (=\ |:ra:152:1|\ l))}\ \ \ \text{(assert\ (=\ a\ |:ra:152:1|))}\ \ \ \text{(assert\ (not\ (=\ a\ l)))}\]
+
 \subsection{Result of the running example}
@@
 }
+\QIN{
+We get the final result after pruning all the unsatisfiable open transitions, 2/3 of the intermediate results; the resulting open automaton is shown in Fig.~\ref{schema:ccs-result}, we give out the open automaton manually through drawing the final result open transitions generated by algorithm.
+A part of results we computed by hand in advance are also list below.
+The $ot_1$ represents the value-passing between $a.P$ and $b.Q$ and they are synchronized then give out an silent action $\tau$, process $P$ and $Q$ should not work in this case.
+The $ot_3$ and $ot_5$ represent another possible path to execute $a.P||b.Q$, action $a$ and $b$ are finished in sequence instead of synchronizing, they are just transmitted out as the external action.
+The behavior of the processes, presented as holes $P$ and $Q$ in this pNet, is uncertain, we only know the sort $Action$ for them.
+So the action from $P$ might be synchronized with the action $b$ that is what $ot_9$ presents or be directly transmitted to the external as the $ot_7$ shows.
+And we can see more cases of the interaction between these two process in the open transitions start at the state $11$, synchronizing two actions like $ot_{13}$ or directly transmitting like $ot_{15}$.
+}
+
+\QIN{
+To sum up, from the pNet encoding CCS formula inputed by the user we generate the open transitions and prune the unsatisfiability automatically.
+The final result open transitions represent all the possible movements of the CCS example.
+They can exactly construct the open automaton for the given example.
+}
 
@@
 $\begin{array}{@{}r@{}l@{}}
-    ot_1  = &\openrule{\{0 \xrightarrow{a} 1, 0 \xrightarrow{b} 1\}, ~~a=ich(v_{11}) \!\land\! b=ch(v_{11}) \!\land\! a\neq l \!\land\! b\neq r\!\land\! v_1=\tau}
+    ot_1  = &\openrule{\{0 \xrightarrow{a}_{C_1} 1, 0 \xrightarrow{b}_{C_2} 1\}, ~~a=!ch_{11}(v_{11}) \!\land\! b=?ch_{11}(v_{11}) \!\land\! a\neq l \!\land\! b\neq r\!\land\! v_1=\tau}
     {\ostate{00} \xrightarrow{v_1} \ostate{11}}\\
@@
 $\begin{array}{@{}r@{}l@{}}
-    ot_3  = &\openrule{\{0 \xrightarrow{a} 1\}, ~~a\neq l \!\land\! v_3=a}
+    ot_3  = &\openrule{\{0 \xrightarrow{a}_{C_1} 1\}, ~~a\neq l \!\land\! v_3=a}
     {\ostate{00} \xrightarrow{v_3} \ostate{10}}\\
-    ot_5  = &\openrule{\{0 \xrightarrow{b} 1\}, ~~b\neq r \!\land\! v_5=b}
+    ot_5  = &\openrule{\{0 \xrightarrow{b}_{C_2} 1\}, ~~b\neq r \!\land\! v_5=b}
     {\ostate{10} \xrightarrow{v_5} \ostate{11}}\\
@@
 $\begin{array}{@{}r@{}l@{}}
-    ot_7  = &\openrule{\{1 \xrightarrow{l} 1\}, ~~\{\xrightarrow{hb_{17}}\}, ~~v_7=hb_{17}}
+    ot_7  = &\openrule{\{1 \xrightarrow{l}_{C_1} 1\}, ~~\{\xrightarrow{hb_{17}}\}, ~~v_7=hb_{17}}
     {\ostate{10} \xrightarrow{v_7} \ostate{10}}\\
@@
 $\begin{array}{@{}r@{}l@{}}
-    ot_9  = &\openrule{\{0 \xrightarrow{b} 1, 1 \xrightarrow{l} 1\}, ~~\{\xrightarrow{hb_{19}}\}, ~~b=ich(v_{19}) \!\land\! b\neq r \!\land\! hb_{19}= ch(v_9)\!\land\! v_9=\tau}
+    ot_9  = &\openrule{\{0 \xrightarrow{b}_{C_2} 1\}, ~~\{\xrightarrow{hb_{19}}\}, ~~b=!ch_{19}(v_{19}) \!\land\! b\neq r \!\land\! hb_{19}=?ch_{19}(v_{19})\!\land\! v_9=\tau}
     {\ostate{10} \xrightarrow{v_9} \ostate{11}}\\
@@
 $\begin{array}{@{}r@{}l@{}}
-    ot_{13}  = &\openrule{\{1 \xrightarrow{l} 1, 1 \xrightarrow{r} 1\}, ~~\{\xrightarrow{hb_{113}}, \xrightarrow{hb_{213}}\}, ~~hb_{113}= ich(v_{13}) \!\land\!
-hb_{213}= ch(v_{13}) \!\land\!
+    ot_{13}  = &\openrule{\{1 \xrightarrow{l}_{C_1} 1, 1 \xrightarrow{r}_{C_2} 1\}, ~~\{\xrightarrow{hb_{113}}, \xrightarrow{hb_{213}}\}, ~~hb_{113}= !ch_{113}(v_{113}) \!\land\!
+hb_{213}=?ch_{113}(v_{113}) \!\land\!
 v_{13}=\tau}
@@
 $\begin{array}{@{}r@{}l@{}}
-    ot_{15}  = &\openrule{\{1 \xrightarrow{l} 1\}, ~~\{\xrightarrow{hb_{115}}\}, ~~v_{15}=hb_{115}}
+    ot_{15}  = &\openrule{\{1 \xrightarrow{l}_{C_1} 1\}, ~~\{\xrightarrow{hb_{115}}\}, ~~v_{15}=hb_{115}}
     {\ostate{11} \xrightarrow{v_{15}} \ostate{11}}\\
@@
   work}
+\QIN{
+In this paper we presented the algorithm of generating the open automaton for the open pNet involving the implementation part of the algorithm.
+Our implementation includes two main parts.
+First, we compute all the possible open transitions.
+The actions in pLTS and hole behaviors are composed in the algorithm while the generation of predicate need to match the combinations of the subnets with the synchronization vectors.
+Then we ensure the correctness of the intermediate result.
+The method use a SMT solver Z3 for checking the satisfiability of the open transitions using the predicate of them.
+In order to do that, we have done some translation on the presentation, the predicate and the assignments of the variables which are also considered as a part of predicates before submitting them to the Z3.
+We implemented our algorithm in the VerCors platform and use some running examples, the formula from other process algebras, to test the algorithm.
+The result of the running examples are shown as the open automaton with all the parameters generated by the algorithm automatically.
+The open automaton successfully presents all the possible movement of the formula.
+}
 
@@
   implement simplification)}
+\QIN{
+This paper raises the question of the efficiency and performance of the SMT solvers.
+It is not ensured that Z3 is the best one, in fact, there is some problem during the implementation the checking method using Z3.
+For example, if the $functions$ and the $datatypes$ independent to each other, checking the $assertions$ is a simple work.
+However, $functions$ on recursive $datatypes$ make it more complex, some special rules might be defined by user for the induction.
+}
+
+\QIN{
+The next work after the generation of the open automaton of the pNet is planned to check the bisimulation of the pNets.
+In previous paper, we have already found the FH-bisimulaiton\cite{meiji-sccs} as a prototype.
+We will decide the definition of the bisimulation of the pNets and the algorithm to prove a relation between two pNets is a bisimulation.
+Before that work, we need to refine the result open transitions, eliminating the redundancy in the predicate of the result.
+The ideal result is what we showed in the bottom part of Fig.~\ref{schema:ccs-result} while there is many intermediate variables we used, such as fresh local variables of synchronization vectors, and fresh result variables of intermediate open transitions, in the algorithm for the propagation of the actions or values.
+So far, to eliminate the intermediate variables in the predicate, we define the range of the significant variables that we won't eliminated: the local variables of pLTS transitions, the hole behaviors and the result action at the top level.
+}
 

### 2017-03-27 2017-Xudong-SMT/OpenPNets-SMT.tex
Check all bleu part till page 19

@@
 %
-
-\begin{example} \emph{Using the operational rules to compute
-    open-transitions}
-  In Fig. \ref{usingrules:OT11} we show the deduction tree used to construct and prove the 
-  open transition $OT_{11}$ of \texttt{CCS} (see example page
-  \pageref{OT:ccs-composed}).
-%  \TODO{Eric: change for a deduction tree of CCS expression}
-\ERIC{  The proof tree uses TR1 for the $l$ transition of $C_1$ and for the
-  $b$ transition of $C_2$, then uses an action $b_P$ of hole $P$, then
-  combines the results using the second vector of the PN2 sub-pNet, and
-  the third vector of the top node. This yields a final $\tau$
-  transition. The deduction tree in the figure shows how the
-  predicates are generated in this process. 
-}
-
 \begin{figure}[tb]
@@
   \caption{Proof of  $OT_{11}$ (with interaction of processes $P$ and action $b$) for ``a.P||b.Q''}
-  \label{usingrules:OT2}
+  \label{usingrules:OT11}
 \end{figure}
 
+\begin{example} \emph{Using the operational rules to compute
+    open-transitions}
+  In Fig. \ref{usingrules:OT11} we show the deduction tree used to construct and prove the 
+  open transition $OT_{11}$ of \texttt{CCS} (see example page
+  \pageref{OT:ccs-composed}).
+%  \TODO{Eric: change for a deduction tree of CCS expression}
+The proof tree uses TR1 twice, for the $l$ transition of $C_1$ and for the
+  $b$ transition of $C_2$, then uses an action $b_P$ of hole $P$, and
+  combines the results using the second vector of the PN2 sub-pNet, and
+  the third vector of the top node. This yields a final $\tau$
+  transition. The deduction tree in the figure shows how the
+  predicates are generated in this process.
+
 \end{example}
 
-Note that while the scenario above is expressed as a single
-instantiation of the possible behaviours, the constructions below are
-kept symbolic, and each open-transition deduced expresses a whole family of
-behaviours, for any possible values of the variables.
+%% Note that while the scenario above is expressed as a single
+%% instantiation of the possible behaviours, the constructions below are
+%% kept symbolic, and each open-transition deduced expresses a whole family of
+%% behaviours, for any possible values of the variables.
 
@@
 
-\TODO{Refine the algorithm description}
-
 \begin{alg}[Behavioural semantics of open pNets: Sketch]
@@
 
-%3) this ends with the "while" from step 2, when we have no more
-%unexplored set.
 \end{alg}
@@
 
+In the following sections, we detail:
+\begin{itemize}
+\item The structure of fresh variable names.
+\item The details of the implementation for step 2a-2b, refined into:
+  \subitem combining all possibilities of subnets activity/inactivity,
+  \subitem matching each combination with synchronisation vectors.
+\item Management of local variables of pLTSs.
+\item Pruning of unsatisfiable open transitions using the Z3 SMT solver.
+\end{itemize}
+
 \subsection{Fresh variables}
@@
 
-\TODO{Add the process and the vector ids ?}
-
-\QIN{
+\TODO{Option: Add the process and the vector ids ?}
+
 $Prefix$ avoids the confusion between variables from different structures with the same name by attaching the type of the structure.
@@
 $A\ set\ of\ counters$ is used to count the current times the SV, Hole, subnet invoked, or the number of possible OT generated to provide an identity.
-}
-
-\subsection{Predicate generation}
-\QIN{
-The predicate of the open transition is a conjunction of two parts every time applying Tr2.
-One part composes the predicate from the subnets and the guard from transitions in sub-pLTS or synchronization vectors.
-The other part is the conjunction of equations generating during  synchronizing subnets' behaviors and synchronization vectors.
-Note that it is simple to collect required terms in the first part while in the second part it need to find out all the possible conjunction forms.
-We present here a algorithm divided in two step.
-Combining enumerates all the possible combinations of the working status.
-Matching synchronizes the subnets according to synchronization vectors to generate possible predicates.
-}
+
+\subsection{Combining and Matching using TR2}
+
+The predicate of the open transition is a conjunction of two parts
+every time applying Tr2. One part composes the predicate from the
+subnets and the guard from transitions in sub-pLTS or synchronization
+vectors. The other part is the conjunction of equations generated
+during matching the subnets' behaviors with the synchronization
+vectors. Note that it is simple to collect required terms in the first
+part while in the second part we need to find out all the possible
+conjunction forms. We present here a algorithm divided in two
+step. Combining enumerates all the possible combinations of the
+working status. Matching synchronizes the subnets according to
+synchronization vectors to generate possible predicates.
+
 %Combining is to generate all the possible matchings of the subnets' OTs (open transitions). The result list of the matched tuples called *combination*.
@@
 \paragraph{Combining}
-\QIN{
-We first conduct combining.
-To each subnet, we enumerate all the possible cases of its working status.
-The result action of a pLTS or a pNet is the external action of the node shows the working status of it.
-The hole whose behavior is uncertain doesn't have an exact external presentation of action.
-We only give a variable to each hole and treat it as hole behavior to suppose working status of the hole.
-Here should have a constraint that this variable belongs to the sort of hole.
-In every case, the hole behaviors are unchanged, so we only make the combinations of subnets' open transitions.
-}
-
-\QIN{
+
+We first conduct combining. For each subnet, we enumerate all the
+possible cases of its working status. The result action of a pLTS or a
+pNet is the external action of the node shows the working status of
+it.
+
+For holes, their behavior is unspecified, it doesn't have an exact
+external presentation of action. We only give an action variable to each hole
+and treat it as hole behavior to suppose working status of the
+hole.
+% Here should have a constraint that this variable belongs to the sort of hole.
+In every case, the hole behaviors are unchanged, so we
+only make the combinations of subnets' open transitions.
+
 Algorithm 1 shows the combining algorithm for enumerating all the possible combinations of open transitions.
 The algorithm initializes an empty list $L_C$.
-Dealing with the list $TR$ containing several sets of open transitions from different subnets, the algorithm only chooses one of sets $L_{ot}$ and does combining on the rest part of $TR$ recursively then get a partial result of combining, $L'_C$.
+Dealing with the list $TR$ containing several sets of open transitions from different subnets, the algorithm only chooses one of sets $L_{ot}$ and does combining on the remaining part of $TR$ recursively then get a partial result of combining, $L'_C$.
 Since there could exist the case that the subnet is not working, a $null$ is added into the $L_{ot}$ to represent it.
 We get much more combinations after combining $ot$ from $L_{ot}$ with the partial result.
-}
 
@@
 
-\Require List $TR$ of result open transition sets from the subnets. 
+\Require The list $TR$ of the open transition sets of the subnets. 
 \Ensure The list of all the possible combinations of open transitions $L_C$.
-\State Initial an empty combination list $L_C$;
+\State Initialise an empty combination list $L_C$;
 \State Extract a list of open transitions $L_{ot}$ from $TR$;
-\State Insert $null$ into $L_{ot}$;
+\State Add $null$ to $L_{ot}$;
 \State Get the combinations $L'_C$ of the $TR$;
@@
 \paragraph{Matching}
-\QIN{
+
 We now come to the matching using combinations from the previous step, together with hole behaviors and the result action, to match with the synchronization vectors.
-}
-
-\QIN{
-Algorithm 2 shows the algorithm matches combination $L_C$, hole behaviors $B$ with synchronization vectors $SV$.
-Every time we choose a synchronization vector $sv$ from $SV$ for matching, we clone it and use the cloned one $sv'$.
+
+Algorithm 2 shows the algorithm matches combination $L_C$, hole
+behaviors $B$ with synchronization vectors $SV$. Remember variables
+inside a synchronisation vector are consider local to the vector; so every time we choose a synchronization vector $sv$ from $SV$ for matching, we clone it and use the cloned one $sv'$.
 We use the definition declared before to construct all the possible predicates but the algorithm has not checked the correctness of these predicates.
-It needs a further refinement.
-}
-
-\QIN{
-In order to filter a part of mismatches, at any time an action $e_1$ matching with an element $e_2$ from synchronization vector, the pair $(e_1, e_2)$ must be checked: if both $e_1$ and $e_2$ are $null$ or $not\ null$, then it continues to generate a new term of predicate.
-Otherwise, it is intuitive that the working status coming from the subnet $e_1$ is different from what asked by the synchronization vector $e_2$, then this case is filtered.
-}
+
+There is one mismatch case we can easily detect here, that is its
+working status:
+At any time an action $e_1$ matching with an element $e_2$ from
+synchronization vector, the pair $(e_1, e_2)$ must be checked: if both
+$e_1$ and $e_2$ are $null$ or $not\ null$, then it continues to
+generate a new term of predicate. Otherwise, it is intuitive that the
+working status coming from the subnet $e_1$ is different from what
+asked by the synchronization vector $e_2$, then this case is filtered
+out.
+
+Then we build the resulting open transition. Satisfiability of the
+predicate is not checked at this level, but only later, at the
+toplevel of the pNet.
+
 \begin{algorithm}
@@
 \subsection{Management of assignments}
-\QIN{
-The pLTS contains some variables in its states, or just as global states of the pLTS, with several assignments.
-The algorithm composing assignments from subnets is different from the generation of predicates.
-When applying Tr1, we just keep the assignments in the Post of the open transition.
-And when it comes to Tr2, Post is the union of the assignments propagate from the subnets.
-The assignments provide value of the variables in predicates.
-There is usually not only one assignments for a variable and the assignment will lose when the algorithm computes other open transitions using other transitions in pLTS.
-The values of the variables are necessary for checking satisfiability of the open transitions together with predicates, miss of them may drop the unsatisfiable results.
-In order to avoid such mistakes, the algorithm manages the variables together with its all possible assignments.
-}
-
-\QIN{
-We use a list of triad $<v,\ S, \ AssignRH>$ for each pLTS to record the information of the state variables of the pLTS where $v$ is the state variable in pLTS, $S$ is its owner state and $AssignRH$ is a list of expressions over other variables in the right hand side of assignments of $v$.
-The $S$ can be $null$ in the record triad, but it means the variable is global in the pLTS belonging to all the states instead of meaning it belongs to nothing.
+The pLTS contains some variables in each of its states (state
+variables), or just as global states of the pLTS (global variables).
+Both can be assigned in the pLTS transitions.
+The algorithm composing assignments from subnets is different from the
+generation of predicates. When applying Tr1, we just keep the
+assignments in the Post of the open transition. And when it comes to
+Tr2, Post is the union of the assignments propagate from the
+subnets. The assignments provide value of the variables in
+predicates.
+There is usually not only one assignment for a state variable as
+several incoming transitions of a state can perform different
+assignments on the same variable. The values of the
+variables are necessary for checking satisfiability of the open
+transitions together with predicates, miss of them may drop the
+unsatisfiable results. In order to avoid such mistakes, the algorithm
+manages the variables together with a list of all its possible assignments.
+
+We use a list of triples $<v,\ S, \ AssignRH>$ for each pLTS to record
+the information of both state and global variables of the pLTS where $v$ is the  variable in pLTS, $S$ is its owner state and $AssignRH$ is a list of expressions over other variables in the right hand side of assignments of $v$.
+The $S$ can be $null$ in the record triple, but it means the variable is global in the pLTS belonging to all the states instead of meaning it belongs to nothing.
 So it should be noted that the changing of the value of the global state variable every time a transition is conducted.
 $AssignRH$ is the collection of all the possible expressions coming from the the right hand side of assignments.
-It keeps the information of the assignments for each state variable.
-We update the list of record triad every time Tr1 is applied, adding the right side of the assignments into corresponding expression lists.
+It keeps the information of the assignments for each variable.
+We update the list of record triples every time Tr1 is applied, adding the right side of the assignments into corresponding expression lists.
 So the list keeps the all the assignments in the pLTS.
 Then we can track all the possible value of the variables when computing open transitions.
-The initial value of the state variable is also seemed as an assignment for that variable.
-We must give a initial value to the global state variable or there will be some problem in the start state.
-However, we sometimes don't give initial values to the state variables (except the global variables) as their initial values are decided by their first assignments, default values for them is hard to decide manually.
-}
+The initial value of the state variable is also seen as an assignment
+for that variable. We must give a initial value to the global state
+variable or there will be some problem in the start state. However, we
+sometimes don't give initial values to the state variables (except the
+global variables) as their initial values are decided by their first
+assignments. Checking whether each variable is initialized before
+being used is a separated problem, that should be done before starting
+our algorithm.
 
 \subsection{Pruning the unsatisfiable results}
-\QIN{
-We have used a brute-force method to generate all the possible open transitions in the open automaton.
-It obviously contains some of unsatisfiability in the open transitions.
-In Fig~\ref{schema:unsat-ot}, we show an unsatisfiable open transition from the result of the CCS running example.
-It presents the case that the top level transmits out the action from the PN2, formula $a.P$, as this time only PN2 is working and C1 is performing action $a$ when hole $P$ is also working.
-In this case, the second synchronization vector of PN2, transmitting the behavior from hole $P$ to the higher level, is used while it is obviously violate the guard of the vector.
-So we can easily find the contradiction between the generated predicate term $ra:152:1=l \!\land\!
-a=:ra:152:1$ and the guard composed into the predicate $a \neq l$.
-To get a correct open automaton of the pNet, such unsatisfiable open transitions need to be eliminated.
-We choose a SMT solver Z3 as the checker for the open transitions considering the predicates may contain the expression using uninterpreted functions declared by users.
-}
+
+We have used a brute-force method to generate all the possible open
+transitions in the open automaton. It obviously contains some of
+unsatisfiability in the open transitions. In
+Fig~\ref{schema:unsat-ot}, we display an unsatisfiable open transition
+from the result of the CCS running example. It shows the case that the
+top level transmits out the action from the PN2, formula $a.P$, as
+this time only PN2 is working and C1 is performing action $a$ when
+hole $P$ is also working. When matching this case against the second
+synchronization 
+vector of PN2, transmitting the behavior from hole $P$ to the higher
+level, is used while it is obviously violate the guard of the
+vector. So we can easily find the contradiction between the generated
+predicate term $ra:152:1=l \!\land\! a=:ra:152:1$ and the guard
+composed into the predicate $a \neq l$.
+
+To get a correct open
+automaton of the pNet, such unsatisfiable open transitions need to be
+eliminated. This is not easy to perform directly inside our
+algorithm, in particular because it requires some symbolic computation
+on the action expressions and the predicates, and that this reasonning
+may depend on the specific theory of the action algebra. 
+We choose a SMT solver Z3 as the checker for the open
+transitions considering the predicates may contain the expression
+using uninterpreted functions declared by users.
+The ``Modulo Theory'' part of SMT solvers is important here, so that
+the solver can use specific properties of the action algebra.
+
 \begin{figure}[t]
@@
   \end{array}$
-\caption{One of the unsatisfiable open transitions in CCS running example)}  \label{schema:unsat-ot}
+\caption{One of the unsatisfiable open transitions in CCS running example}  \label{schema:unsat-ot}
 \end{figure}
@@
 \paragraph{Interaction with Z3}
-\TODO{1. example input of Z3 in SMT-LIB.[DONE] 2. software architecture.[DONE]}
-\QIN{
-We implement the dynamic interaction between the pNet API and Z3 solver through its JAVA API.
-But here we present the code in Z3 by SMT-LIB language instead of JAVA codes to make it easier to read.
-In Fig~\ref{schema:smt-lib}, we show the manual input of the unsatisfiable result before.
+%\TODO{1. example input of Z3 in SMT-LIB.[DONE] 2. software architecture.[DONE]}
+There are several ways to interact with the Z3 solver. 
+It is possible to use Z3 interactively using the SMT-LIB
+(Python-based) language. From inside our algorithm code, 
+we implement the dynamic interaction between the pNet API and Z3
+solver through its JAVA API. But here we present the code in Z3 by
+SMT-LIB language instead of JAVA codes to make it easier to read. In
+Fig~\ref{schema:smt-lib}, we show the  input of the unsatisfiable
+result before.
+The input starts with the declaration of the CCS action algebra types
+and constructors.
 Some $datatypes$ are declared to input the sorts of the CCS example, here we only declare one $datatypes$ named $Action$ to involve all the constant actions.
@@
 In the output, "(not and)" shows Z3 have found out the contradiction in the predicate and the result "unsat" is just what we expected.
-}
-
-\QIN{
-We present the architecture of the interaction with Z3 in Fig~\ref{schema:interaction}.
-Both two parts need to be translated before submitting to the Z3.
-The $presentation$ of the pNet is declared at the beginning of the algorithm as the $sorts$ and the $operators$ will be used throughout the whole algorithm.
-It is translated into $datatypes$ and $functions$ then submitted to the Z3 at the same time.
-The predicate will be translated into $assertions$ before submitted to Z3 after the algorithm computing out all the possible open transitions, they act as intermediate results there.
+
+We present the architecture of the interaction with Z3 in
+Fig~\ref{schema:interaction}.
+For each OT generated at the toplevel of a pNet, the predicate must be
+submitted for satisfiability check to Z3. For that we need to
+translate into Z3 (Java-API) syntax, both the elements of the action
+algebra, and the predicates itself, including the encoding of the
+variable assignments (the Post part).
+
+The $presentation$ of the action algebra
+is declared at the beginning of the algorithm as the $sorts$ and the
+$operators$ will be used throughout the whole algorithm. It is
+translated into $datatypes$ and $functions$ then submitted to the Z3
+at the same time.
+Each candidate predicate will then be translated into $assertions$ before submitted to Z3 after the algorithm computing out all the possible open transitions, they act as intermediate results there.
 Together with the $datatypes$ and $functions$, the $assertions$ are used to check the satisfiability of the predicate in Z3.
-}
-
-\paragraph{Translation of presentation}
-\QIN{
+
+\paragraph{Translation of Action algebra presentation}
+
 The $datatypes$ are declared according to the $sorts$ the users declared in the $presentation$.
@@
 For example, we define a new operator to present the equation between two actions in CCS example $\text{EQUAL}$ in the format likes:
-}
+
 \[< Action , Action > \rightarrow Bool .\]
-\QIN{
+
 It will be translated into the Z3 statement:
-}
+
 \[\text{(declare-fun\ EQUAL\ (Action\ Action)\ Bool) .}\]
@@
 \paragraph{Translating assignments into predicate terms}
-\QIN{
-The assignments are also taken into account when checking the satisfiability of the open transitions as they present the value of the variables.
-In order to do that, we employs a translation from assignments into term of predicates.
-The assignments required to be translated are only those belong to the variables contain the in the start states of the open transitions.
-The assignments are represented as equations between the variables and the expressions on the right side of assignment.
-For the assignments of the same variable, we do not figure out which state is the precursor of current state, we keep all these possible equations instead, and generate the disjunction of these equations.
-The state could always move to the target state if there exists one of the values of its variable satisfies the guard.
-It won't matter the variable of the next state except that the right side expression contain its variables.
-This is a problem left to be solved in our future work.
-After that, for the assignments of the different variables, we generate a conjunction of them.
-This way we obtain a new term of the predicate involving assignments of the variables.
-}
+
+The assignments are also taken into account when checking the
+satisfiability of the open transitions as they represent the value of
+the variables involved in an OT. In order to do that, we employs a
+translation from assignments into term of predicates. The assignments
+required to be translated are only those belong to the variables
+contain in the start states of the open transitions. The assignments
+are represented as equations between the variables and the expressions
+on the right side of assignment. For the assignments of the same
+variable, we do not figure out which state is the precursor of current
+state, we keep all these possible equations instead, and generate the
+disjunction of these equations. The state could always move to the
+target state if there exists one of the values of its variable
+satisfies the guard.
+\TODO{It won't matter the variable of the next state
+except that the right hand side expression contain its variables. This
+is a problem left to be solved in our future work. WHICH PROBLEM ?}
+After that, for the assignments of the different variables, we generate a conjunction of them. This way we obtain a new term of the predicate involving assignments of the variables.
 
 \paragraph{checking satisfiability}
-\TODO{After we get the result OTs, for each result OT, declare the variables and assertions in the Java API. Conduct checking method and get the result.[DONE]\\}
-\QIN{
-We check the satisfiability of open transitions on the top level of the pNet, treating these open transitions as the intermediate result of the algorithm.
-After we get the intermediate results of open transitions, we check them one by one.
+
+% We check the satisfiability of open transitions on the top level of
+% the pNet, treating these open transitions as the intermediate result
+% of the algorithm. After we get the intermediate results of open
+% transitions, we check them one by one.
 Here we declare the variables in the predicate first to make Z3 know all the parameters used for checking this time.
@@
 The variables can declared using the $datatypes$ declared in the format as:
-}
+
 \[\text{(declare-const\ a\ Action) .}\]
 
-\QIN{
-The predicate submitted to the Z3 contain the assignments as them become a part of predicate after our translation.
-Each term of the predicate is an assertion in Z3, as an example, in the former unsatisfiable result, the contradiction is occured in terms:
-}
+The predicate submitted to the Z3 contain the assignments as them
+become a part of predicate after our translation. Each term of the
+predicate is an assertion in Z3, as an example, in the former
+unsatisfiable result in Fig~\ref{schema:unsat-ot}, the contradiction is occured in terms:
+
 \[(:ra:152:1 = l) \land (a = :ra:152:1) \land (l \neq a) .\]
-\QIN{
+
 from which we generate following three assertion:
-}
+
 \[\text{(assert\ (=\ |:ra:152:1|\ l))}\ \ \ \text{(assert\ (=\ a\ |:ra:152:1|))}\ \ \ \text{(assert\ (not\ (=\ a\ l)))}\]
@@
 \label{section:full-result}
-\TODO{
-Xudong: full result of the tool execution on the running example\\\\
-Open Automata of the CCS example.
+% \TODO{
+% Xudong: full result of the tool execution on the running example\\\\
+% Open Automata of the CCS example.
+\TODO{The open automaton is not the final one. The vectors are wrong,
+  and you should add at least the OT name... 
 }

### 2017-03-27 2017-Xudong-SMT/OpenPNets-SMT.tex
structure

@@
 
-\ERIC{imported from FORTE'16, }
-
 In the nineties, several 
@@
 
+\TODO{say that apart from the old work by J. Rathke, we know no other
+  research addressing our goals, and especially no attempts to develop
+  an algorithmic treatment of such symbolic systems by interacting
+  with automatic theorem provers}.
+
+\TODO{Then you can list the ATP/ITP you have mentionned Coq, Isabelle,
+  B-tools, or others like CVC4, as possible alternative to Z3}
+
 \paragraph{Structure.}
+In \ref{section:examples} we present two simple examples taht will be
+running examples to illustrate all parts of the paper. Then in the
+background section
+\ref{section:pnets} we give a description and a formal definition of
+the pNet model, as found in previous publications.
+Section \ref{section:op-semantics} recalls the operationnal semantics
+of pNet, including its structural rules, and a sketch of the algorithm
+to compute such semantics, but also explains the enhancment we have
+done to these definitions.
+Section \ref{section:implementation} explains in details our
+implementation within the Vercors plateform, and shows the full result of
+the semantic computation on one of the running examples.
+Finally we conclude and discuss perspectives in section
+\ref{section:conclusion}.
 
 \section{Running Examples}
+\label{section:examples}
+
 Several publications \cite{HMZ:PDP15,henrio:Forte2016} already have introduced
@@
 \section{Implementation}
+\label{section:implementation}
 The VerCors platform uses (closed) pNets as the intermediate language
@@
 
-\TODO{Option: Add the process and the vector ids ?}
+%\TODO{Option: Add the process and the vector ids ?}
 

### 2017-03-28 2017-Xudong-SMT/OpenPNets-SMT.tex
The introduction (incompleted)
The contribution and related work are not finished.

@@
   We implement the symbolic semantics of open pNets using their
-  so-called ``Open Automaton'' behavioural semantics. This involve
-  building predicates expressing the synchronisation conditions
+  so-called ``Open Automaton'' behavioral semantics. This involve
+  building predicates expressing the synchronization conditions
   allowing some combination of events in the pNet system. These
@@
 
+\QIN{
+pNets (Parameterized Networks of Synchronized Automata) was proposed to give a behavioral specification formalism for distributed systems.
+It is used in the VerCors, a platform for designing and verifying distributed systems, as the intermediate language for the high-level language.
+This language formalizes each component of the distributed system and gives out the composition of these components.
+At the beginning, pNet can be used to formalize full defined systems or softwares.
+The open pNet is proposed to solve the problem of the uncertain components contained in the systems using "holes" as the process parameter dealing with these components.
+The hole acts as the placeholder for the uncertain component with a set of possible behaviors the component might conduct, presenting the "open" property.
+}
+
+\QIN{
+The pNet has developed in a series of works~\cite{HMZ:PDP15,henrio:Forte2016} and some examples has been introduced showing its ability in encoding the operators from some other algebras or the program skeletons.
+It is just the first step of our long-term goals.
+The operational semantic of the open pNet has already defined, but we only have a sketch about how to compute it and have no implementation.
+The operational semantic here is defined as an open automaton.
+The open transitions in the open automaton presenting the composition feature of the pNet is the main part of the open automaton computing and needs to satisfy several constraints.
+So in the computing algorithm, computing open transitions is necessary and should have some method to keep them satisfying the constraints.
+Then implementation of the algorithm should be finished.
+After getting the open automaton of the pNet, we can check the equivalence between pNets.
+The equivalence between pNets is "FH-bisimulation" taking the predicate of the open transitions into account each time matching such open transitions.
+In our long-term goals, the final target is to check the property of open systems.
+}
+
 In the nineties, several 
-works extended the basic behavioural models based on labelled
-transition systems to address value-passing or parameterised systems, using
+works extended the basic behavioral models based on labelled
+transition systems to address value-passing or parameterized systems, using
 various symbolic encodings of the
@@
 In \cite{Linconcur96}, H.M. Lin addressed value-passing calculi, for which he
-developed a symbolic behavioural semantics, and proved algebraic properties.
+developed a symbolic behavioral semantics, and proved algebraic properties.
 Separately J. Rathke~\cite{HennessyRathke:TCS98} defined another
 symbolic semantics for 
-a parameterised broadcast calculus, together with strong and weak bisimulation
+a parameterized broadcast calculus, together with strong and weak bisimulation
 equivalences, and developed a symbolic model-checker based on a tableau
@@
 \paragraph{Contribution}
+\QIN{
+This paper shows that
+}
 
@@
 
-\TODO{Then you can list the ATP/ITP you have mentionned Coq, Isabelle,
+\TODO{Then you can list the ATP/ITP you have mentioned Coq, Isabelle,
   B-tools, or others like CVC4, as possible alternative to Z3}
@@
 \paragraph{Structure.}
-In \ref{section:examples} we present two simple examples taht will be
+In \ref{section:examples} we present two simple examples that will be
 running examples to illustrate all parts of the paper. Then in the
@@
 the pNet model, as found in previous publications.
-Section \ref{section:op-semantics} recalls the operationnal semantics
+Section \ref{section:op-semantics} recalls the operational semantics
 of pNet, including its structural rules, and a sketch of the algorithm
-to compute such semantics, but also explains the enhancment we have
+to compute such semantics, but also explains the enhancement we have
 done to these definitions.
 Section \ref{section:implementation} explains in details our
-implementation within the Vercors plateform, and shows the full result of
+implementation within the Vercors platform, and shows the full result of
 the semantic computation on one of the running examples.
@@
 operators of various classical process algebras, or more complex
-synchronisation structures in distributed or parallel languages.
+synchronization structures in distributed or parallel languages.
 In this section, we use two process expressions, respectively from CCS
@@
   ``<act, \_ > -> act'', in which ``\_'' means that the corresponding
-  subnet is not involved in this synchronisation.
+  subnet is not involved in this synchronization.
   There is also a difference with the usual CCS notation of
-  input/output actions: in the first vector, $ich$ and $ch$ are
+  input/output actions: in the first vector, $!ch$ and $ch$ are
   corresponding input and output channels (see next section for a more
@@
   Remark that these 4
-  synchronisation vectors correspond faithfully to the usual SOS
+  synchronization vectors correspond faithfully to the usual SOS
   rules of CCS operational semantics.
@@
   Each of the subnets act as one of the prefix operator.
-In each of them there is a parameterised labelled transition system
+In each of them there is a parameterized labelled transition system
 (pLTS) and a hole. The pLTS is a controller managing the
@@
 only possible transition performs the action variable $a$; once in
-state 1, the controler can perform (infinitely often) action $l$ that
+state 1, the controller can perform (infinitely often) action $l$ that
 is a constant action local to C1 (that must be different from any
-other actino of the whole system). In the node PN2, there are 2
-synchronisation vectors, the first one transmits to the upper level the
+other action of the whole system). In the node PN2, there are 2
+synchronization vectors, the first one transmits to the upper level the
 action $a$ (and thanks to C1, will only be activated one time); the
@@
 It should be easy to see that this pNet system encodes properly the
-behavioural semantics of the corresponding CCS expression. Remarkk
+behavioral semantics of the corresponding CCS expression. Remark
 that it is built in a systematic structural way, one pNet node
-encoding each CCS operator. And it is parameterised both at the level
-of actions variables (occuring within the controllers and the synchronisation
+encoding each CCS operator. And it is parameterized both at the level
+of actions variables (occurring within the controllers and the synchronization
 vectors), and at the level of process parameters 
@@
 operator of the LOTOS language. For the readers not familiar with
-Lotos, the pNet encodingss here should be sufficient to understand the
+Lotos, the pNet encodings here should be sufficient to understand the
 Enable operator semantics.
@@
 In fact we give two encodings of this operator: the first one is
-``state oriented'', in the sense that the controler has two states,
+``state oriented'', in the sense that the controller has two states,
 indicating where the control point is in the P>>Q process expression,
 either in P or in Q. The transition between these occurs when process
-P performs a $\delta(x)$ action, transfering the control to Q, and
+P performs a $\delta(x)$ action, transferring the control to Q, and
 sending a value $x$ at the same time. Process Q must be ready to
-``accept'' this value through an $acc(x)$ action. The controler C1,
-and the 3 synchronisation vectors of the Enable1 pNet should be easy
+``accept'' this value through an $acc(x)$ action. The controller C1,
+and the 3 synchronization vectors of the Enable1 pNet should be easy
 to understand. Note 
@@
 the node controller is encoded in the value of the pLTS state
-variable(s). Here we have a single state variable $s_0$, initialised
+variable(s). Here we have a single state variable $s_0$, initialized
 as $0$. Its value is ``0'' when the control is on P, and ``1'' when the
@@
 $\underline{\delta(y_2)}$ result action, where the underlined action
-stands for an internal (already synchronised) action, that cannot be
-further synchronised at upper levels. This is a straighforward
-generalisation of the notion of internal actions, that will be
+stands for an internal (already synchronized) action, that cannot be
+further synchronized at upper levels. This is a straightforward
+ generalization of the notion of internal actions, that will be
 convenient for observing internal events during model-checking.
 
-\section{Parameterised Networks (pNets): definition}
+\section{parameterized Networks (pNets): definition}
 \label{section:pnets}
@@
 pNets are tree-like structures, where the leaves are either
-\emph{parameterised labelled transition systems (pLTSs)}, expressing the
-behaviour of basic processes, or \emph{holes}, used as placeholders
+\emph{parameterized labelled transition systems (pLTSs)}, expressing the
+behavior of basic processes, or \emph{holes}, used as placeholders
 for unknown processes, of which we only specify the set of possible
 actions, this set is named the \emph{sort}.
-Nodes of the tree (pNet nodes) are synchronising artifacts, using a
-set of \emph{synchronisation vectors} that express the possible
-synchronisation between the parameterised actions of a subset of the
+Nodes of the tree (pNet nodes) are synchronizing artifacts, using a
+set of \emph{synchronization vectors} that express the possible
+synchronization between the parameterized actions of a subset of the
 sub-trees.
@@
 \paragraph*{Term algebra.}
-Our models rely on a notion of parameterised actions, that are
+Our models rely on a notion of parameterized actions, that are
 symbolic expressions using data types and variables. As our model aims
-at encoding the low-level behaviour of possibly very different
+at encoding the low-level behavior of possibly very different
 programming languages, we do not want to impose one specific algebra
@@
 expressions, to express various kinds of communication or
-synchronisation mechanisms.
+synchronization mechanisms.
 
@@
 \cite{Milner89} or of usual point-to-point message passing calculi, but it also allows
-for more general mechanisms, like gate negociation in Lotos, or broadcast
+for more general mechanisms, like gate negotiation in Lotos, or broadcast
 communications.
@@
 %For Lotos-style
-%distributed synchronisation, we use synchronisation vectors that encode matching data
+%distributed synchronization, we use synchronization vectors that encode matching data
 %offers on a common gate; or 
 We can also use more complex action structure such as Meije-SCCS action
-monoids, like in $a.b$, $a^{f(n)}$ (see \cite{deSimone85}). The expressiveness of the synchronisation constructs
+monoids, like in $a.b$, $a^{f(n)}$ (see \cite{deSimone85}). The expressiveness of the synchronization constructs
 will depend on the action algebra.
@@
 manipulated, defined, or accessed inside states, actions, guards, and
-assignments. Without loss of generality and to simplify the formalisation, we suppose 
+assignments. Without loss of generality and to simplify the formalization, we suppose 
 here that 
@@
 $\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in J}\rangle$,
-where $\alpha \in\AlgA$ is a parameterised action, $e_b \in
+where $\alpha \in\AlgA$ is a parameterized action, $e_b \in
 \AlgB$ is a guard, and the variables $x_j\in P$
@@
 Now we define
-pNet nodes, as constructors for hierarchical behavioural structures.
+pNet nodes, as constructors for hierarchical behavioral structures.
 A pNet has a set of sub-pNets that can be either pNets or pLTSs, and a
@@
 a set of actions, each of them triggering internal actions in each of
-the sub-pNets. The synchronisation between global actions and
-internal actions is given by  \emph{synchronisation vectors}: a
-synchronisation vector synchronises one or several internal actions, and
+the sub-pNets. The synchronization between global actions and
+internal actions is given by  \emph{synchronization vectors}: a
+synchronization vector synchronises one or several internal actions, and
 exposes a single resulting global action.
-Actions involved at the pNet level (in the synchronisation vectors) do
+Actions involved at the pNet level (in the synchronization vectors) do
 not need to distinguish between input and output
@@
 \item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
-  synchronisation vectors ($K\in\I_\P$). $\forall k\!\in\! K,
+  synchronization vectors ($K\in\I_\P$). $\forall k\!\in\! K,
   \symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k$ where
@@
 $\mylangle\overline{\pNet},\overline{S},\symb{SV}_k^{k\in K} \myrangle$
-be a pNet. Consider a synchronisation vector $SV_k$, for $k\in K$. We define a
+be a pNet. Consider a synchronization vector $SV_k$, for $k\in K$. We define a
 predicate $\Pred$ relating
@@
   The second rule deals with pNet nodes: for each possible
-  synchronisation vector applicable to the rule subject, the premisses
+  synchronization vector applicable to the rule subject, the premisses
   include one {\em open transition} for each sub-pNet involved, one possible
@@
   leaves of the pNet, not only those involved in the chosen
-  synchronisation vector.
+  synchronization vector.
 
@@
 \paragraph{Variable management.}
-The variables in each synchronisation vector are considered local:
+The variables in each synchronization vector are considered local:
 for a given pNet expression, we must have fresh local variables for
@@
 
-\begin{alg}[Behavioural semantics of open pNets: Sketch]
+\begin{alg}[behavioral semantics of open pNets: Sketch]
 This is a standard residual algorithm over a set of open-automaton
@@
 rules Tr1 and Tr2, using all applicable combinations
-of synchronisation vectors.
+of synchronization vectors.
 
@@
 algorithm terminates. The following theorem shows that an open-pNet
-with finite synchronisation sets, finitely many leaves and
+with finite synchronization sets, finitely many leaves and
 holes, and each pLTS at leaves having a finite number of states and
@@
 Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
-  J}$, if the sets $L$ and $J$ are finite, if the synchronisation vectors of all pNets 
+  J}$, if the sets $L$ and $J$ are finite, if the synchronization vectors of all pNets 
   included in  $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ 
@@
   \subitem combining all possibilities of subnets activity/inactivity,
-  \subitem matching each combination with synchronisation vectors.
+  \subitem matching each combination with synchronization vectors.
 \item Management of local variables of pLTSs.
@@
 behaviors $B$ with synchronization vectors $SV$. Remember variables
-inside a synchronisation vector are consider local to the vector; so every time we choose a synchronization vector $sv$ from $SV$ for matching, we clone it and use the cloned one $sv'$.
+inside a synchronization vector are consider local to the vector; so every time we choose a synchronization vector $sv$ from $SV$ for matching, we clone it and use the cloned one $sv'$.
 We use the definition declared before to construct all the possible predicates but the algorithm has not checked the correctness of these predicates.
@@
 
-\ERIC{Optionally, simplify the predicate by eliminating the unnecessary intermediate variables, that were produced as fresh local variables of synchronisation vectors, and fresh result variables of intermediate OTs.
+\ERIC{Optionally, simplify the predicate by eliminating the unnecessary intermediate variables, that were produced as fresh local variables of synchronization vectors, and fresh result variables of intermediate OTs.
 In the resulting predicate the only significant variables are :\\

### 2017-03-29 2017-Xudong-SMT/OpenPNets-SMT.tex
small typos
many todo and blue stuff

@@
 
-\QIN{
-pNets (Parameterized Networks of Synchronized Automata) was proposed to give a behavioral specification formalism for distributed systems.
-It is used in the VerCors, a platform for designing and verifying distributed systems, as the intermediate language for the high-level language.
-This language formalizes each component of the distributed system and gives out the composition of these components.
-At the beginning, pNet can be used to formalize full defined systems or softwares.
-The open pNet is proposed to solve the problem of the uncertain components contained in the systems using "holes" as the process parameter dealing with these components.
-The hole acts as the placeholder for the uncertain component with a set of possible behaviors the component might conduct, presenting the "open" property.
-}
-
-\QIN{
-The pNet has developed in a series of works~\cite{HMZ:PDP15,henrio:Forte2016} and some examples has been introduced showing its ability in encoding the operators from some other algebras or the program skeletons.
-It is just the first step of our long-term goals.
-The operational semantic of the open pNet has already defined, but we only have a sketch about how to compute it and have no implementation.
-The operational semantic here is defined as an open automaton.
-The open transitions in the open automaton presenting the composition feature of the pNet is the main part of the open automaton computing and needs to satisfy several constraints.
-So in the computing algorithm, computing open transitions is necessary and should have some method to keep them satisfying the constraints.
-Then implementation of the algorithm should be finished.
-After getting the open automaton of the pNet, we can check the equivalence between pNets.
-The equivalence between pNets is "FH-bisimulation" taking the predicate of the open transitions into account each time matching such open transitions.
-In our long-term goals, the final target is to check the property of open systems.
-}
-
 In the nineties, several 
@@
 
-\paragraph{Context}
-\TODO{
-  Summary of previous works on pNets and open pNets => 1/2 page.\\
-  Longterm goals:\\
-  - open pNets to represent operators and program skeletons (ref to
-  \cite{HMZ:PDP15})\\
-  - compute semantics in term of open transitions\\
-  - compute equivalence (bisimulation of open automata)\\
-  - model-check properties of open systems
-  }
-\paragraph{Contribution}
-\QIN{
-This paper shows that
-}
+Parameterized Networks of Synchronized Automata (pNets) were proposed
+to give a behavioral specification formalism for distributed
+systems, synchronous, asynchronous, or heterogeneous. It is used in
+VerCors, a platform for designing and 
+verifying distributed systems, as the intermediate language for various
+high-level languages. The high-level languages in VerCors formalize
+each component of the 
+distributed system and gives out the composition of these
+components.
+pNets provides the core low-level semantic formalism for VerCors, and
+is made of a hierarchical composition of (value-passing) automatas,
+called parameterized labelled transition systems (pLTS), where each
+hierarchical level defines the possible synchronisation of the lower levels.
+Traditionaly, pNet have been used to formalize full
+defined systems or softwares. But we want also to define and reason
+about incompletely defined systems, like program skeletons, operators,
+or open expressions of process calculi.
+The open pNet is proposed to solve the
+problem of the undefined components contained in the systems using
+"holes" as the process parameter dealing with these components. The
+hole acts as the placeholder for the uncertain component with a set of
+possible behaviors the component might conduct, presenting the "open"
+property.
+
+The pNet model was developed in a series of
+works~\cite{HMZ:PDP15,henrio:Forte2016} and some examples have been
+introduced showing its ability in encoding the operators from some
+other algebras or  program skeletons. It is just the first step of
+our long-term goals. The operational semantic of the open pNet has
+already been defined, but we only had a sketch about how to compute it and
+had no implementation. This operational semantic is defined as an
+Open Automaton in which Open Transitions contain logical predicates
+expressing the relations between the behavior of the holes, and the
+global behavior of the system.
+
+Computing the open transitions from the composition of pNet is the
+main part of the open 
+automaton computing and needs to satisfy the constraints expressed as
+the rules of the operationnal semantics. So in
+the computing algorithm, computing open transitions is necessary and
+should have some method to keep them satisfying the constraints.
+Computing open automata by hand is complicated and error prone. And
+the algorithm published in \cite{henrio:Forte2016} was not precise
+enough for an implementation. Our first goal was then to refine the
+algorithm, and implement it in a tool.
+In the long goal, we want to be able to check the equivalence between
+pNets. The equivalence between pNets is "FH-bisimulation" taking the
+predicate of the open transitions into account each time matching such
+open transitions. In our long-term goals, the final target is to check
+the property of open systems.
+
+Our contribution in the article is:
+\begin{itemize}
+\item We have refined the open automaton generation algorithm, to make
+  it implementable, and we implemented a full working prototype, within the
+  VerCors platform. In the process, we had to improve slightly the
+  semantics rules, and to add features in the algorithm to deal with
+  management of variables and assignements.
+  \item parameterisation over the action algebra operators in the
+    VerCors ECORE and library
+  \item interaction with the Z3 SMT solver
+    \item validation on several use-cases
+\end{itemize}
+
+\TODO{I have not described the items above after th efirst one, left
+  it to you...}
 
@@
 
-\ERIC{Keep minimum defs here too be independent from FORTE}
+% \ERIC{Keep minimum defs here too be independent from FORTE}
 
@@
 communications.
-\ERIC{Formally, value-passing actions \emph{\`a la} CCS, denoted as ``?ch(x)'' and ``!ch(exp)'' in our CCS running example, stand respectively for $CCSact(i(ch),?x)$ and $CCSact(ch,exp)$, where $ch$ is a variable denoting a channel name, $?x$ is an input variable denoting the data argument received as input on $ch$, and $exp$ some data expression (containing no input variables).
+Formally, value-passing actions \emph{\`a la} CCS, denoted as ``?ch(x)'' and ``!ch(exp)'' in our CCS running example, stand respectively for $CCSact(i(ch),?x)$ and $CCSact(ch,exp)$, where $ch$ is a variable denoting a channel name, $?x$ is an input variable denoting the data argument received as input on $ch$, and $exp$ some data expression (containing no input variables).
 In our example we will use the usual CCS syntax.
-}
 %For Lotos-style
@@
 %  \TODO{ERIC: change for an OT of CCS example}
-\ERIC{  The \texttt{CCS} pNet of Fig.
+The \texttt{CCS} pNet of Fig.
 \ref{schema:ccs-pnets} has 2 controllers and 2 holes.
 We show its full open Automaton in section \ref{section:full-result}, it has 16 open transitions.
-We detail 3 of them here:}
+We detail 3 of them here:
 
@@
                       }
-     {\ostate{00} \xrightarrow{\underline{\tau}} \ostate{10}}$
+     {\ostate{00} \xrightarrow{\underline{\tau}} \ostate{11}}$
 
@@
                       }
-     {\ostate{10} \xrightarrow{a} \ostate{11}} $
+     {\ostate{10} \xrightarrow{a} \ostate{10}} $
 
@@
                        0 \xrightarrow{b}_{C_2} 1 ~~
-                       \{ \xrightarrow{b_P}_{P} \}               ~~
-                 [ a\neq l \land b\neq r \land b_P=?ch(v) \land b=!ch(v) ]              
+                       \{ \xrightarrow{hb_P}_{P} \}               ~~
+                 [ a\neq l \land b\neq r \land hb_P=?ch(v) \land b=!ch(v) ]              
                       }
@@
 \end{example}
-\TODO{Eric: short comments}
+
+The first open transitions listed, $OT_1$ and $OT_3$, only involve
+possible actions from the prefix operators, respectively communication
+between the two prefixes, if actions $a$ and $b$ are matching emit and
+receive actions on the same channel; or simple propagation of action
+$a$ from the left prefix, with no special constraint other than being
+different from the local $l$ action of pLTS $C_1$.
+
+Remark the structured states in the conclusion of these rules: both
+start in state $\ostate{00}$, where both $C_1$ and $C_2$ are in their
+initial states. They end in different structured states, because in
+$OT_1$ both pLTS chage states, meaning that the control has gone
+respectively to processes $P$ and $Q$, consuming actions $A$ and $B$,
+while in $OT_3$ only $C_1$ has moved.
+
+The last open transition $OT_{11}$ starts in state $\ostate{10}$, with
+control at $P$ on the left, and action $b$ on the right. So these two
+can communicate, e.g. here if $b$ is an emission, and the action of hole
+$P$ is the matching reception.
 
@@
 
-from which we generate following three assertion:
+from which we generate the following three assertions:
 
@@
 % Open Automata of the CCS example.
-\TODO{The open automaton is not the final one. The vectors are wrong,
-  and you should add at least the OT name... 
-}
-\QIN{
-We get the final result after pruning all the unsatisfiable open transitions, 2/3 of the intermediate results; the resulting open automaton is shown in Fig.~\ref{schema:ccs-result}, we give out the open automaton manually through drawing the final result open transitions generated by algorithm.
-A part of results we computed by hand in advance are also list below.
-The $ot_1$ represents the value-passing between $a.P$ and $b.Q$ and they are synchronized then give out an silent action $\tau$, process $P$ and $Q$ should not work in this case.
-The $ot_3$ and $ot_5$ represent another possible path to execute $a.P||b.Q$, action $a$ and $b$ are finished in sequence instead of synchronizing, they are just transmitted out as the external action.
-The behavior of the processes, presented as holes $P$ and $Q$ in this pNet, is uncertain, we only know the sort $Action$ for them.
-So the action from $P$ might be synchronized with the action $b$ that is what $ot_9$ presents or be directly transmitted to the external as the $ot_7$ shows.
-And we can see more cases of the interaction between these two process in the open transitions start at the state $11$, synchronizing two actions like $ot_{13}$ or directly transmitting like $ot_{15}$.
-}
-
-\QIN{
-To sum up, from the pNet encoding CCS formula inputed by the user we generate the open transitions and prune the unsatisfiability automatically.
-The final result open transitions represent all the possible movements of the CCS example.
-They can exactly construct the open automaton for the given example.
-}
+
+We get the final result after pruning all the unsatisfiable open
+transitions, that is 2/3 of the intermediate results; the resulting open
+automaton is shown in Fig.~\ref{schema:ccs-result}, we have drawn
+manually the open automaton obtained as the final result generated by
+algorithm.
+The $ot_1$ represents the
+value-passing between $a.P$ and $b.Q$ and they are synchronized then
+give out an silent action $\tau$, process $P$ and $Q$ should not work
+in this case. The $ot_3$ and $ot_5$ represent another possible path to
+execute $a.P||b.Q$, action $a$ and $b$ are finished in sequence
+instead of synchronizing, they are just transmitted out as the
+external action. The behavior of the processes, presented as holes $P$
+and $Q$ in this pNet, is uncertain, we only know the sort $Action$ for
+them. So the action from $P$ might be synchronized with the action $b$
+that is what $ot_9$ presents or be directly transmitted to the
+external as the $ot_7$ shows. And we can see more cases of the
+interaction between these two processes in the open transitions starting at
+the state $11$, synchronizing two actions like $ot_{13}$ or directly
+transmitting like $ot_{15}$.
+
+To sum up, from the pNet encoding CCS formula inputed by the user we
+generate the open transitions and prune the unsatisfiability
+automatically. The final result open transitions represent all the
+possible movements of the CCS example. They can exactly construct the
+open automaton for the given example.
+
+\TODO{Beware, there are incoherences between the automaton and the
+  rules, e.g. OT3 goes to state 01, or 01 ?}
 
@@
 The next work after the generation of the open automaton of the pNet is planned to check the bisimulation of the pNets.
-In previous paper, we have already found the FH-bisimulaiton\cite{meiji-sccs} as a prototype.
+In previous paper, we have already found the FH-bisimulaiton\cite{deSimone85} as a prototype.
 We will decide the definition of the bisimulation of the pNets and the algorithm to prove a relation between two pNets is a bisimulation.

### 2017-03-29 2017-Xudong-SMT/OpenPNets-SMT.tex
Introduction finished.
Finish the introduction of the paper.

--- 2017-03-28 2017-Xudong-SMT/OpenPNets-SMT.tex
@@
 \section{Introduction}
-
-\QIN{
-pNets (Parameterized Networks of Synchronized Automata) was proposed to give a behavioral specification formalism for distributed systems.
-It is used in the VerCors, a platform for designing and verifying distributed systems, as the intermediate language for the high-level language.
-This language formalizes each component of the distributed system and gives out the composition of these components.
-At the beginning, pNet can be used to formalize full defined systems or softwares.
-The open pNet is proposed to solve the problem of the uncertain components contained in the systems using "holes" as the process parameter dealing with these components.
-The hole acts as the placeholder for the uncertain component with a set of possible behaviors the component might conduct, presenting the "open" property.
-}
-
-\QIN{
-The pNet has developed in a series of works~\cite{HMZ:PDP15,henrio:Forte2016} and some examples has been introduced showing its ability in encoding the operators from some other algebras or the program skeletons.
-It is just the first step of our long-term goals.
-The operational semantic of the open pNet has already defined, but we only have a sketch about how to compute it and have no implementation.
-The operational semantic here is defined as an open automaton.
-The open transitions in the open automaton presenting the composition feature of the pNet is the main part of the open automaton computing and needs to satisfy several constraints.
-So in the computing algorithm, computing open transitions is necessary and should have some method to keep them satisfying the constraints.
-Then implementation of the algorithm should be finished.
-After getting the open automaton of the pNet, we can check the equivalence between pNets.
-The equivalence between pNets is "FH-bisimulation" taking the predicate of the open transitions into account each time matching such open transitions.
-In our long-term goals, the final target is to check the property of open systems.
-}
-
 In the nineties, several 
@@
   }
+
+\QIN{
+pNets (Parameterized Networks of Synchronized Automata) was proposed to give a behavioral specification formalism for distributed systems.
+It is used in the VerCors, a platform for designing and verifying distributed systems, as the intermediate language for the high-level language.
+This language formalizes each component of the distributed system and gives out the composition of these components.
+At the beginning, pNet can be used to formalize full defined systems or softwares.
+The open pNet is proposed to solve the problem of the uncertain components contained in the systems using "holes" as the process parameter dealing with these components.
+The hole acts as the placeholder for the uncertain component with a set of possible behaviors the component might conduct, presenting the "open" property.
+}
+
+\QIN{
+The pNet has developed in a series of works~\cite{HMZ:PDP15,henrio:Forte2016} and some examples has been introduced showing its ability in encoding the operators from some other algebras or the program skeletons.
+It is just the first step of our long-term goals.
+The operational semantic of the open pNet has already defined, but we only have a sketch about how to compute it and have no implementation.
+The operational semantic here is defined as an open automaton.
+The open transitions in the open automaton presenting the composition feature of the pNet is the main part of the open automaton computing and needs to satisfy several constraints.
+So in the computing algorithm, computing open transitions is necessary and should have some method to keep them satisfying the constraints.
+Then implementation of the algorithm should be finished.
+After getting the open automaton of the pNet, we can check the equivalence between pNets.
+The equivalence between pNets is "FH-bisimulation" taking the predicate of the open transitions into account each time matching such open transitions.
+And several automatic theorem provers solver will also take part in the bisimulation checking algorithm.
+In our long-term goals, the final target is to check the property of open systems.
+}
+
 \paragraph{Contribution}
 \QIN{
-This paper shows that
+This paper presents our open automaton computing algorithm and its implementation in pNet API.
+Comparing the result of the algorithm with the manual result on the running example shows that the algorithm works properly in computing the open automaton for the pNet.
+The algorithm contains the method computing the open transitions composing the transitions from the subnets according to several defined rules the open transitions need to satisfy.
+These results are not the final results in fact, they still contain some unsatisfiable results we need to eliminate.
+To eliminate those unsatisfiability, we interact with an automatic theorem provers to use them for satisfiability checking.
+The translation of the pNet, mainly its presentation and its open transition predicates, is required for the implementation of the interaction.
 }
@@
 \paragraph{Related works}
-
 \TODO{say that apart from the old work by J. Rathke, we know no other
@@
   B-tools, or others like CVC4, as possible alternative to Z3}
+
+\QIN{
+There is not much researches try developing the symbolic bisimulation for the value-passing process algebra, as our long-term goals, especially no algorithm treatment of the symbolic systems developed by interacting with automatic theorem provers.
+The closest work is an old work from J.
+Rathke~\ref{HennessyRathke:TCS98}, who developed the symbolic bisimulaiton (both weak and strong bisimulation) on a calculus of broadcasting system (CBS).
+The CBS is similar with classic process calculi such as CCS, CSP, communicating by broadcasting values, one-to-many communication instead of one-to-one communication and transmitting values without blocks.
+That makes the definition of the symbolic semantic and bisimulation equivalence different from the classic works.
+}
+
+\QIN{
+There are many automatic theorem provers developed in previous works we can consider to use for the result pruning and bisimulation checking in our algorithm, such as Z3~\ref{}, Coq~\ref{}, Isabelle~\ref{} or Rodin~\ref{} as possible alternative.
+Z3 is developed by Microsoft Research based on the satisfiability modulo theories (SMT), mainly applied in extended static checking, test case generation, and predicate abstraction.
+Tools like Coq, Isabelle and Rodin have already integrated SMT solvers as modules for proving the theorem or formula inputed by users.
+}
 

### 2017-03-29 2017-Xudong-SMT/OpenPNets-SMT.tex
Introduction.
Merge introduction into the newest version.

--- 2017-03-29 2017-Xudong-SMT/OpenPNets-SMT.tex
@@
 
+\QIN{
+This paper presents our open automaton computing algorithm and its implementation in pNet API.
+Comparing the result of the algorithm with the manual result on the running example shows that the algorithm works properly in computing the open automaton for the pNet.
+The algorithm contains the method computing the open transitions composing the transitions from the subnets according to several defined rules the open transitions need to satisfy.
+These results are not the final results in fact, they still contain some unsatisfiable results we need to eliminate.
+To eliminate those unsatisfiability, we interact with an automatic theorem provers to use them for satisfiability checking.
+The translation of the pNet, mainly its presentation and its open transition predicates, is required for the implementation of the interaction.
+}
+
 \paragraph{Related works}

### 2017-03-29 2017-Xudong-SMT/OpenPNets-SMT.tex
todos and conclusion

@@
 algebra. The input and output should belong to the sorts on the
-pNet. When there are $k$ sorts in this pNet, the structure of a
+pNet. When there are $k$ subnets in this pNet, the structure of a
 $n$-ary operator is vector as $< Sort_{i_1}, ... , Sort_{i_n} >
 \rightarrow Sort_j , i_1 , ... , i_n, j \in [0..k] $.
-\TODO{ I do not understand this. As discussed today, I will wait till
-  you include an example of algebra presentation before rewriting the comment.}
 
@@
 
-\TODO{give an example of user-defined sorts/operators, and tell that
-  you will give it's translation into Z3 in section 5.4}
+%\TODO{give an example of user-defined sorts/operators, and tell that
+%  you will give it's translation into Z3 in section 5.4}
 
@@
 satisfies the guard.
-\TODO{It won't matter the variable of the next state
-except that the right hand side expression contain its variables. This
-is a problem left to be solved in our future work. WHICH PROBLEM ?}
+%\TODO{It won't matter the variable of the next state
+%except that the right hand side expression contain its variables. This
+%is a problem left to be solved in our future work. WHICH PROBLEM ?}
 After that, for the assignments of the different variables, we generate a conjunction of them. This way we obtain a new term of the predicate involving assignments of the variables.
@@
 
-\TODO{Conclusion: what you have accomplished, clearly state your
-  contributions, and what is delivered at the end of your internship
-  work}
-\QIN{
-In this paper we presented the algorithm of generating the open automaton for the open pNet involving the implementation part of the algorithm.
-Our implementation includes two main parts.
-First, we compute all the possible open transitions.
-The actions in pLTS and hole behaviors are composed in the algorithm while the generation of predicate need to match the combinations of the subnets with the synchronization vectors.
-Then we ensure the correctness of the intermediate result.
-The method use a SMT solver Z3 for checking the satisfiability of the open transitions using the predicate of them.
-In order to do that, we have done some translation on the presentation, the predicate and the assignments of the variables which are also considered as a part of predicates before submitting them to the Z3.
-We implemented our algorithm in the VerCors platform and use some running examples, the formula from other process algebras, to test the algorithm.
-The result of the running examples are shown as the open automaton with all the parameters generated by the algorithm automatically.
-The open automaton successfully presents all the possible movement of the formula.
-}
+In this paper we presented the algorithm for generating an open
+automaton representing the semantics of an open pNet, and we described
+the implementation of the
+algorithm. Our implementation includes two main parts. First, we
+compute all the possible open transitions. The actions in pLTS and
+hole behaviors are composed in the algorithm while the generation of
+predicate need to match the combinations of the subnets with the
+synchronization vectors. Some of the open transitions obtained at this
+intermediate step, constructed in a structural manner from all
+possible combinations of possible logical predicates, may
+contain predicates which do not represent any possible concrete
+instanciations. 
+To get rid of these useless transtions, we use a SMT solver Z3 for checking the
+satisfiability of the predicate in each open transition. In
+order to do that, we have done some translation on the presentation,
+the predicate and the assignments of the variables which are also
+considered as a part of predicates before submitting them to the
+Z3 solver. We implemented our algorithm in the VerCors platform and use some
+running examples, the formula from other process algebras, to test the
+algorithm. The result of the running examples are shown as the open
+automaton with all the parameters generated by the algorithm
+automatically. The open automaton successfully presents all the
+possible movement of the formula.
 

### 2017-03-29 2017-Xudong-SMT/OpenPNets-SMT.tex
discussion

@@
 automatically. The open automaton successfully presents all the
-possible movement of the formula.
+possible movements of the CCS expression.
 
@@
   implement simplification)}
-\QIN{
-This paper raises the question of the efficiency and performance of the SMT solvers.
-It is not ensured that Z3 is the best one, in fact, there is some problem during the implementation the checking method using Z3.
-For example, if the $functions$ and the $datatypes$ independent to each other, checking the $assertions$ is a simple work.
-However, $functions$ on recursive $datatypes$ make it more complex, some special rules might be defined by user for the induction.
-}
-
-\QIN{
-The next work after the generation of the open automaton of the pNet is planned to check the bisimulation of the pNets.
-In previous paper, we have already found the FH-bisimulaiton\cite{deSimone85} as a prototype.
-We will decide the definition of the bisimulation of the pNets and the algorithm to prove a relation between two pNets is a bisimulation.
-Before that work, we need to refine the result open transitions, eliminating the redundancy in the predicate of the result.
-The ideal result is what we showed in the bottom part of Fig.~\ref{schema:ccs-result} while there is many intermediate variables we used, such as fresh local variables of synchronization vectors, and fresh result variables of intermediate open transitions, in the algorithm for the propagation of the actions or values.
-So far, to eliminate the intermediate variables in the predicate, we define the range of the significant variables that we won't eliminated: the local variables of pLTS transitions, the hole behaviors and the result action at the top level.
-}
-
-=> Simplification is not yet implemented. It is not strictly required
-for the Open Automaton construction, but it will be critical later for
-predicate comparison in the bisimulation algorithm.
-
-\ERIC{Optionally, simplify the predicate by eliminating the unnecessary intermediate variables, that were produced as fresh local variables of synchronization vectors, and fresh result variables of intermediate OTs.
-In the resulting predicate the only significant variables are :\\
-- the input variables of pLTS transitions\\
-- the actions of holes\\
-- the result action at toplevel.}
+
+Among the questions arides during this work, an important one is the
+efficiency of Z3 for our needs. Z3 is famous for being very fast for
+solving very large sets of assertions, and this could be important for
+us. But we encountered  some problems during the implementation the
+checking method using Z3. For example, if the $functions$ and the
+$datatypes$ part of the algebra presentation we submit to the solver
+are independent with each other, then checking the $assertions$ is a
+simple work. However, $functions$ on recursive $datatypes$ make it
+more complex, some special rules might be defined by user for the
+induction. Also, we need more evidence that dealing with more complex
+action algebras, that would involve axiomatizing their dat structures
+into Z3 theories, will indeed allow us to decide validity of
+predicates.
+We may also try other automatic theorem provers, depending on th
+estructure of the proofs we need.
+
+Naturally, the next work after the generation of the open automata
+will be to check the bisimulation of the pNets. In previous paper, we
+have already found the FH-bisimulation, inspired by~\cite{deSimone85} as a
+suitable definition. Usual approaches of bisimulation by partition
+refinement does not work easily with symbolic transitions. In a first
+step we may want instead to define and implement an algorithm fo
+rchecking that a given equivalence relation between open automata
+states is indeed a FH-Bisimulation. Finding automaticaly a
+bisimulation relation or the most general bisimulation will be more
+challenging. It appears also that when comparing different pNets with
+different structure, strong bisimulation will be too strong a notion,
+and that we will have to define proper notinos of weak equivalence or
+refinements.
+
+Before that work, we need to reconsider the result open transitions
+from our algorithm. The ideal
+result that we showed in the bottom part of
+Fig.~\ref{schema:ccs-result} is not the one generated by the algorithm,
+because it contains many intermediate
+variables, such as fresh local variables of synchronization
+vectors, and fresh result variables of intermediate open transitions.
+Such intermediate variables come from the way predicates are
+generated, and depends on the particular structure of the pNet. But
+they are not significant in the resulting behavior, and should be
+eliminated before comparing such behavior with another pNet.
+To eliminate the intermediate variables in the predicate, we want to define
+the set of the significant variables that we won't eliminate: the
+local variables of pLTS transitions, the hole behaviors and the result
+action at the top level.
+The result of the elimination will be simpler predicates, that can be
+successfuly compared (e.g. by Z3) within the bisimulation checking
+algorithm.
 

### 2017-03-29 2017-Xudong-SMT/OpenPNets-SMT.tex
finished introduction

@@
 equivalences, and developed a symbolic model-checker based on a tableau
-method for these processes. 30 years later, no
+method for these processes. Thirty years later, no
 practical verification approach and no verification platform are
@@
 
-Our contribution in the article is:
+This paper presents our open automaton computing algorithm and its
+implementation using the pNet API. Comparing the result of the algorithm with
+the manual result on our running examples shows that the algorithm
+works properly in computing the pNet semantics. The
+algorithm contains the method computing the open transitions composing
+the transitions from the subnets according to several defined rules
+the open transitions need to satisfy. These results are not the final
+results in fact, because they contain some unsatisfiable results we need
+to eliminate. To eliminate those unsatisfiability, we interact with an
+automatic theorem prover for satisfiability checking.
+
+\paragraph{Contribution}
+In the article we show how:
 \begin{itemize}
@@
   management of variables and assignements.
-  \item parameterisation over the action algebra operators in the
-    VerCors ECORE and library
-  \item interaction with the Z3 SMT solver
-    \item validation on several use-cases
+  \item We extended the meta-model of action expressions, and the
+    associated API, in the VerCors platform, to be able to manage
+    parameterisation over the action algebra operators.
+  \item We have implemented the interaction between our algorithm and the Z3
+    SMT solver, for checking satisfiability of the logical predicates
+    generated by the algorithm.
+    \item We validated the whole approach on several use-cases, taken
+      from two different process languages.
 \end{itemize}
 
-\TODO{I have not described the items above after th efirst one, left
-  it to you...}
-
-\QIN{
-This paper presents our open automaton computing algorithm and its implementation in pNet API.
-Comparing the result of the algorithm with the manual result on the running example shows that the algorithm works properly in computing the open automaton for the pNet.
-The algorithm contains the method computing the open transitions composing the transitions from the subnets according to several defined rules the open transitions need to satisfy.
-These results are not the final results in fact, they still contain some unsatisfiable results we need to eliminate.
-To eliminate those unsatisfiability, we interact with an automatic theorem provers to use them for satisfiability checking.
-The translation of the pNet, mainly its presentation and its open transition predicates, is required for the implementation of the interaction.
-}
-
 \paragraph{Related works}
 
-\TODO{say that apart from the old work by J. Rathke, we know no other
-  research addressing our goals, and especially no attempts to develop
-  an algorithmic treatment of such symbolic systems by interacting
-  with automatic theorem provers}.
-
-\TODO{Then you can list the ATP/ITP you have mentioned Coq, Isabelle,
-  B-tools, or others like CVC4, as possible alternative to Z3}
-
-\QIN{
-There is not much researches try developing the symbolic bisimulation for the value-passing process algebra, as our long-term goals, especially no algorithm treatment of the symbolic systems developed by interacting with automatic theorem provers.
-The closest work is an old work from J.
-Rathke~\ref{HennessyRathke:TCS98}, who developed the symbolic bisimulaiton (both weak and strong bisimulation) on a calculus of broadcasting system (CBS).
-The CBS is similar with classic process calculi such as CCS, CSP, communicating by broadcasting values, one-to-many communication instead of one-to-one communication and transmitting values without blocks.
-That makes the definition of the symbolic semantic and bisimulation equivalence different from the classic works.
-}
-
-\QIN{
-There are many automatic theorem provers developed in previous works we can consider to use for the result pruning and bisimulation checking in our algorithm, such as Z3~\ref{}, Coq~\ref{}, Isabelle~\ref{} or Rodin~\ref{} as possible alternative.
-Z3 is developed by Microsoft Research based on the satisfiability modulo theories (SMT), mainly applied in extended static checking, test case generation, and predicate abstraction.
-Tools like Coq, Isabelle and Rodin have already integrated SMT solvers as modules for proving the theorem or formula inputed by users.
-}
+%% \TODO{say that apart from the old work by J. Rathke, we know no other
+%%   research addressing our goals, and especially no attempts to develop
+%%   an algorithmic treatment of such symbolic systems by interacting
+%%   with automatic theorem provers}.
+
+%% \TODO{Then you can list the ATP/ITP you have mentioned Coq, Isabelle,
+%%   B-tools, or others like CVC4, as possible alternative to Z3}
+
+There is not much researches trying to develop symbolic bisimulation approaches
+for the value-passing process algebra and languages, as our long-term goals,
+especially no algorithm treatment of the symbolic systems developed by
+interacting with automatic theorem provers. The closest work is the
+one already mentionned from J. Rathke~\cite{HennessyRathke:TCS98},
+who developed the symbolic bisimulation for a
+calculus of broadcasting system (CBS). CBS is similar with classic
+process calculi such as CCS and CSP, but communicating by broadcasting
+values, one-to-many communication instead of one-to-one communication
+and transmitting values without blocking. That makes the definition of
+the symbolic semantic and bisimulation equivalence different from the
+classic works.
+
+There are other dedicated platforms, e.g. for the analyses of 
+programming languages, making use of external automatic theorem
+provers (ATP), or even some automatic tactics from interactive theorem
+provers (ITP), to perform symbolic reasonning, and for example to
+discharge some subgoals in the proofs.
+In a similar way, there are several ATPs/ITPs we could consider to use for
+the result pruning and bisimulation checking in our algorithm, as an
+alternative to Z3, such as CVC4~\cite{}, Coq~\cite{},
+Isabelle~\cite{} or others. Z3 is
+developed by Microsoft Research based on the satisfiability modulo
+theories (SMT), mainly applied in extended static checking, test case
+generation, and predicate abstraction. Tools like Isabelle and
+Rodin have already integrated SMT solvers as modules for proving the
+theorem or formula inputed by users.
 

### 2017-03-29 2017-Xudong-SMT/OpenPNets-SMT.tex
last pages

@@
 
-\TODO{Beware, there are incoherences between the automaton and the
-  rules, e.g. OT3 goes to state 01, or 01 ?}
-
 \begin{figure}[h]
@@
 
-\TODO{Discussion: next steps: 1) what is left as open questions on the
-  algorithm itself, what you have learned (is Z3 useful and efficient,
-  is it the right tool ?). 2) next important goal is bisimulation
-  checking, what is neded for that (formalize the algo, define and
-  implement simplification)}
-
-Among the questions arides during this work, an important one is the
+Among the questions arising during this work, an important one is the
 efficiency of Z3 for our needs. Z3 is famous for being very fast for

### 2017-03-30 2017-Xudong-SMT/OpenPNets-SMT.tex
Add references
More references added in .bib.
References have already been cited.
Add the subscript of hb in the page 23.

@@
 the result pruning and bisimulation checking in our algorithm, as an
-alternative to Z3, such as CVC4~\cite{}, Coq~\cite{},
-Isabelle~\cite{} or others. Z3 is
+alternative to Z3, such as CVC4~\cite{barrett:CAV2011}, Coq~\cite{armand:CPP2011,besson:CPP2011},
+Isabelle~\cite{blanchette:FroCoS2011} or others. Z3 is
 developed by Microsoft Research based on the satisfiability modulo
@@
 generation, and predicate abstraction. Tools like Isabelle and
-Rodin have already integrated SMT solvers as modules for proving the
+Rodin~\cite{deharbe2013,deharbe2014,abrial2007} have already integrated SMT solvers as modules for proving the
 theorem or formula inputed by users.

### 2017-04-10 2017-Xudong-SMT/OpenPNets-SMT.tex
Add the example for Presentation
Examples are added in page 13, and corresponding modification in page 20.

@@
 parallel operators of value-passing CCS, and containing two process
-variables (holes) P and Q. In Fig. 1, we show the encoding of this CCS
+variables (holes) P and Q. In Fig.~\ref{schema:ccs-pnets}, we show the encoding of this CCS
 formula. The pNet has a tree-like structure.
@@
           over these objects.
-        \item Constants: The satifiability solver need to know which
-          actions in the pLTS behaviours are constants (like the $l$,
-          $r$ local actions of the controlers in the CCS example). So
+        \item Constants: The satisfiability solver need to know which
+          actions in the pLTS behaviors are constants (like the $l$,
+          $r$ local actions of the controllers in the CCS example). So
           for a given pNet system, the Action sort will include all
@@
 
+\QIN{
+In the CCS example, we have a sort for actions called $Action$:
+}
+
+\[ Action = \{ l, r\} \]
+
 \paragraph{Operators}
@@
 output of the operators used in the expressions from those
-algebra. The input and output should belong to the sorts on the
-pNet. When there are $k$ subnets in this pNet, the structure of a
+algebra. The input and output should belong to the sorts of the
+pNet. When there are $k$ sorts in this pNet, the structure of a
 $n$-ary operator is vector as $< Sort_{i_1}, ... , Sort_{i_n} >
 \rightarrow Sort_j , i_1 , ... , i_n, j \in [0..k] $.
+
+\QIN{For instance, in our CCS running example, there is the action expression $!ch(v)$ using an operator $!$ presenting the ``$EMIT$'' action in CCS.
+We only use a sort called $Action$ to involve all the constant actions or action expressions in pNets and other parameters such as channel $ch$ or variable $v$ are all integers.
+So here we treat $EMIT$ as a binary operator with the format like:
+}
+
+ \[ < Int, Int > \rightarrow Action . \]
 
@@
 improved, including extensions for CCS and LOTOS.
+
+\QIN{The translation of the presentation in the Z3 SMT solver will be given later.
+}
 
@@
 If the return type of the $functions$ is one of the $datatypes$, we add this $function$ when declare the $datatypes$, it present the reality that every action expression also belongs to a sort of pNet.
+
+\QIN{
+So when we declare the operator EMIT we illustrated in section 4.1, it will be just declared together with the constants.
+}
+
  Although in Fig~\ref{schema:smt-lib} we have not declared $functions$, they should be exactly declared if there are new $operators$ declared in the $presentation$.

### 2017-04-12 2017-Xudong-SMT/submit-ICTAC2017.tex
new paper for Ictac

--- 2017-04-10 2017-Xudong-SMT/OpenPNets-SMT.tex
@@
 \begin{abstract}
+  \TODO{not good for a conference, (to be rewriten by Eric)}
   We implement the symbolic semantics of open pNets using their
@@
 
+\TODO{Should be improved}
+
 There is not much researches trying to develop symbolic bisimulation approaches
@@
 synchronization structures in distributed or parallel languages.
-In this section, we use two process expressions, respectively from CCS
-and from Lotos, to illustrate different features of pNets. They will
-serve as running examples in the whole paper.
-
-\subsection{Operators from Classical Process Algebra}
-
-\begin{figure}[h]
-  \centerline{\includegraphics[width=9cm]{XFIG/CCS1}}
-  \caption{The pNet encodings for CCS formula}  \label{schema:ccs-pnets}
-\end{figure}
-
-First example we choose is a formula $a.P||b.Q$, composing prefix and
-parallel operators of value-passing CCS, and containing two process
-variables (holes) P and Q. In Fig.~\ref{schema:ccs-pnets}, we show the encoding of this CCS
-formula. The pNet has a tree-like structure.
-
-The root node of the tree PN1 is the top level of the pNet
-  structure. It acts as the parallel operator. There are two subnets,
-  noted PN2 and PN3, each representing one of the prefix
-  sub-expression. Their behaviors are synchronized in their parent PN1
-  according to a set of synchronization vectors, synchronizing input
-  and output action from these two subnets to give out a silent action
-  $\tau$ or just making the action become visible on the top level when
-  one of the subnets is working alone. The vector concrete syntax is typically
-  ``<act, \_ > -> act'', in which ``\_'' means that the corresponding
-  subnet is not involved in this synchronization.
-  There is also a difference with the usual CCS notation of
-  input/output actions: in the first vector, $!ch$ and $ch$ are
-  corresponding input and output channels (see next section for a more
-  complete formalisation). 
-  Remark that these 4
-  synchronization vectors correspond faithfully to the usual SOS
-  rules of CCS operational semantics.
-
-  Each of the subnets act as one of the prefix operator.
-In each of them there is a parameterized labelled transition system
-(pLTS) and a hole. The pLTS is a controller managing the
-changes of state of the pNet; consider C1, from its initial state the
-only possible transition performs the action variable $a$; once in
-state 1, the controller can perform (infinitely often) action $l$ that
-is a constant action local to C1 (that must be different from any
-other action of the whole system). In the node PN2, there are 2
-synchronization vectors, the first one transmits to the upper level the
-action $a$ (and thanks to C1, will only be activated one time); the
-second one transmit any action of the hole P, but only when C1 can
-perform $l$.
-
-It should be easy to see that this pNet system encodes properly the
-behavioral semantics of the corresponding CCS expression. Remark
-that it is built in a systematic structural way, one pNet node
-encoding each CCS operator. And it is parameterized both at the level
-of actions variables (occurring within the controllers and the synchronization
-vectors), and at the level of process parameters 
-(holes).
-
-\subsection{Open pNet with Assignments in Leaves}
+In this paper, we use a running example inspired from Lotos, to illustrate
+the main features of pNets and the manner we deal with them in the symbolic
+semantics, and in the satifiability checking.
+
 \begin{figure}[h]
@@
 
-In the second running example, we want to illustrate the use of local
-variables in the controller pLTSs. This example is based on the Enable
+This example is based on the Enable
 operator of the LOTOS language. For the readers not familiar with
@@
 Enable operator semantics.
+
+\TODO{To be re-written}
 
@@
 
-\section{parameterized Networks (pNets): definition}
+\section{Background: pNets definition}
 \label{section:pnets}
 
-% \ERIC{Keep minimum defs here too be independent from FORTE}
+\TODO{I have removed some of the technical stuff, adding referemces to Forte'16.
+  We will see if this is enough, and will have to check if this is coherent, and if we can remove more, but for ICTAC, we MUST keep enough formal stuff}
 
@@
 behavior of basic processes, or \emph{holes}, used as placeholders
-for unknown processes, of which we only specify the set of possible
-actions, this set is named the \emph{sort}.
+for unknown processes, of which we only specify their set of possible
+actions, named \emph{sort}.
 Nodes of the tree (pNet nodes) are synchronizing artifacts, using a
@@
 expressions and actions. Moreover, we use a generic {\em action interaction}
-mechanism, based on (some sort of) unification between two or more action
-expressions, to express various kinds of communication or
-synchronization mechanisms.
+mechanism, based on unification between two or more action
+expressions. This will be used in the semantics of synchronisation
+vectors to express various kinds of communication or synchronization mechanisms.
 
@@
 
-pNets can encode naturally the notion of input actions in value-passing CCS
+pNets can encode naturally the notion of input actions as found e.g. in value-passing CCS
 \cite{Milner89} or of usual point-to-point message passing calculi, but it also allows
@@
 communications.
-Formally, value-passing actions \emph{\`a la} CCS, denoted as ``?ch(x)'' and ``!ch(exp)'' in our CCS running example, stand respectively for $CCSact(i(ch),?x)$ and $CCSact(ch,exp)$, where $ch$ is a variable denoting a channel name, $?x$ is an input variable denoting the data argument received as input on $ch$, and $exp$ some data expression (containing no input variables).
-In our example we will use the usual CCS syntax.
-%For Lotos-style
-%distributed synchronization, we use synchronization vectors that encode matching data
-%offers on a common gate; or 
-We can also use more complex action structure such as Meije-SCCS action
-monoids, like in $a.b$, $a^{f(n)}$ (see \cite{deSimone85}). The expressiveness of the synchronization constructs
-will depend on the action algebra.
+\TODO{I removed the CCS input action stuff, check later if we need to
+  replace it here by something different about input action notation}.
+
+%% Formally, value-passing actions \emph{\`a la} CCS, denoted as
+%% ``?ch(x)'' and ``!ch(exp)'' in our CCS running example, stand
+%% respectively for $CCSact(i(ch),?x)$ and $CCSact(ch,exp)$, where $ch$
+%% is a variable denoting a channel name, $?x$ is an input variable
+%% denoting the data argument received as input on $ch$, and $exp$ some
+%% data expression (containing no input variables). In our example we
+%% will use the usual CCS syntax. 
+%% %For Lotos-style
+%% %distributed synchronization, we use synchronization vectors that encode matching data
+%% %offers on a common gate; or 
+%% We can also use more complex action structure such as Meije-SCCS action
+%% monoids, like in $a.b$, $a^{f(n)}$ (see \cite{deSimone85}). The expressiveness of the synchronization constructs
+%% will depend on the action algebra.
 
@@
 assignments. Without loss of generality and to simplify the formalization, we suppose 
-here that 
-variables are local to each 
+here that variables are local to 
 state: each state has its set of variables disjoint from the others. Transmitting 
@@
 pNet nodes, as constructors for hierarchical behavioral structures.
-A pNet has a set of sub-pNets that can be either pNets or pLTSs, and a
+A pNet node has a set of sub-pNets that can be either pNets or pLTSs, and a
 set of Holes, playing the role of process parameters.
@@
 The preceding definition relies on the auxiliary functions below:
+
+\TODO{we do not use the Sort in the implementation of synch vector
+  matching. May be we could remove it from here, but it will not gain
+  much...}
 
@@
   \label{OT:ccs-composed}
-%  \TODO{ERIC: change for an OT of CCS example}
+\TODO{: change for an OT of new Lotos example, may be only one or two
+  of them ?}
 The \texttt{CCS} pNet of Fig.
@@
 %leaves and the holes involved in the rules, but also appearing in  the resulting action.
+
+When building an Open Automaton as the semantics of a pNet, its
+\emph{states}, and the from of the predicates in its
+\emph{transitions} have a specific structure:
 
@@
 
-We build the semantics of open pNets as an open automaton where LTSs are the pLTSs at
+\paragraph{Structural Semantic Rules:}
+Now we build the semantics of an open pNet as an open automaton where LTSs are the pLTSs at
 the leaves of the pNet structure, and the states are given by 
@@
 
+\TODO{Change the example...?}
 \begin{example} \emph{Using the operational rules to compute
@@
  \paragraph{Implementation of the expression meta-model}
+ \TODO{maybe we could remove this paragraph (and the figure)}
 The VerCors platform uses Ecore and EMF to define the structure of
@@
 2b) For each of the obtained deduction trees, extract the resulting
-open-transition, with its predicate and \Post\ assignments by exploring the structure of 
-the pNet.
-
-2c)
+open-transition.
 The predicate is submitted to Z3 for checking satisfiability. If it is
@@
 number of 
-resulting transitions. Then a reachability check could potentialy
-prune the state space.
-
-For each open-transition,  add the transition in the outgoing transitions of
+resulting transitions.
+
+2c) For each open-transition,  add the transition in the outgoing transitions of
 the current state, and add the
@@
 explored set.
+
+3) Finaly a reachability check could potentialy
+prune the state space.
 
@@
 holes, and each pLTS at leaves having a finite number of states and
-(symbolic) transitions, has a finite automaton:
+(symbolic) transitions, has a finite automaton. The proof can be found
+in \cite{henrio:Forte2016}.
 
@@
 
-The proof can be found in \cite{henrio:Forte2016}.
-
 % Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in
@@
   \item Steps 2a-2b are merged, applying Tr2 from the
-premisses OTs from subnets to generate open transitions without
+premisses OTs from subnets to generate OTs without
 explicitely constructing the deduction tree.
-  \item We defined a general naming schema for implementing the fresh 
-and clone functions to rename all the variable to make them unique, but also
+  \item We define a general naming schema for implementing the fresh 
+and clone functions with more structure than a simple global name
+generator. It ensures unicity, but builds names
 readable enough for debugging purpose.
@@
     assignments throughout the whole computation.
-  \item Satisfiability check is done only at
-top level of the open-transition construction. An alternative would be
-to submit the satisfiability check to the SMT solver at each level of
-the hierarchical OT construction, potentially reducing the overall number of
-combinations. But the submission to the SMT engine is costly, and more
-complexity analysis is required before deciding if this would be
-worthwhile. 
+%%   \item Satisfiability check is done only at
+%% top level of the open-transition construction. An alternative would be
+%% to submit the satisfiability check to the SMT solver at each level of
+%% the hierarchical OT construction, potentially reducing the overall number of
+%% combinations. But the submission to the SMT engine is costly, and more
+%% complexity analysis is required before deciding if this would be
+%% worthwhile. 
 \end{itemize}
@@
 \item Management of local variables of pLTSs.
-\item Pruning of unsatisfiable open transitions using the Z3 SMT solver.
+\item Pruning unsatisfiable OTs using the Z3 SMT solver.
 \end{itemize}
@@
 fresh(). 
+\TODO{Could try to reduce the text, but give a couple examples ?}
 
@@
 $A\ set\ of\ counters$ is used to count the current times the SV, Hole, subnet invoked, or the number of possible OT generated to provide an identity.
+
+\TODO{I have not yet been in details through the next section, but we
+  need to shorten them...}
 
@@
 
+\TODO{edit the figure to make it smaller in height}
+
 We present the architecture of the interaction with Z3 in
@@
 automatically. The final result open transitions represent all the
-possible movements of the CCS example. They can exactly construct the
-open automaton for the given example.
+possible movements of the CCS example.
 

### 2017-04-12 2017-Xudong-SMT/OpenPNets-SMT.tex
Add the LOTOS running example.
In appendix.
The description of examples is added.
TODO the analysis of the result.

@@
   There is also a difference with the usual CCS notation of
-  input/output actions: in the first vector, $!ch$ and $ch$ are
+  input/output actions: in the first vector, $!ch$ and $?ch$ are
   corresponding input and output channels (see next section for a more
@@
 \begin{figure}[h]
-
   \includegraphics[width=6cm]{XFIG/Enable1.eps}
@@
   \caption{Two pNet encodings for the Lotos Enable operator P>>Q }  \label{schema:enable-pnets}
-
 \end{figure}
@@
 that the first vector, transmitting an action $a1$ of P, can only
-occur if $a1$ is not a $\delta$.
+occur if $a_1$ is not a $\delta$.
 
@@
 $\begin{array}{@{}r@{}l@{}}
-    ot_7  = &\openrule{\{1 \xrightarrow{l}_{C_1} 1\}, ~~\{\xrightarrow{hb_{17}}\}, ~~v_7=hb_{17}}
+    ot_7  = &\openrule{\{1 \xrightarrow{l}_{C_1} 1\}, ~~\{\xrightarrow{hb_{17}}_P\}, ~~v_7=hb_{17}}
     {\ostate{10} \xrightarrow{v_7} \ostate{10}}\\
@@
 $\begin{array}{@{}r@{}l@{}}
-    ot_9  = &\openrule{\{0 \xrightarrow{b}_{C_2} 1\}, ~~\{\xrightarrow{hb_{19}}\}, ~~b=!ch_{19}(v_{19}) \!\land\! b\neq r \!\land\! hb_{19}=?ch_{19}(v_{19})\!\land\! v_9=\tau}
+    ot_9  = &\openrule{\{0 \xrightarrow{b}_{C_2} 1\}, ~~\{\xrightarrow{hb_{19}}_P\}, ~~b=!ch_{19}(v_{19}) \!\land\! b\neq r \!\land\! hb_{19}=?ch_{19}(v_{19})\!\land\! v_9=\tau}
     {\ostate{10} \xrightarrow{v_9} \ostate{11}}\\
@@
 $\begin{array}{@{}r@{}l@{}}
-    ot_{13}  = &\openrule{\{1 \xrightarrow{l}_{C_1} 1, 1 \xrightarrow{r}_{C_2} 1\}, ~~\{\xrightarrow{hb_{113}}, \xrightarrow{hb_{213}}\}, ~~hb_{113}= !ch_{113}(v_{113}) \!\land\!
+    ot_{13}  = &\openrule{\{1 \xrightarrow{l}_{C_1} 1, 1 \xrightarrow{r}_{C_2} 1\}, ~~\{\xrightarrow{hb_{113}}_P, \xrightarrow{hb_{213}}_Q\}, ~~hb_{113}= !ch_{113}(v_{113}) \!\land\!
 hb_{213}=?ch_{113}(v_{113}) \!\land\!
@@
 $\begin{array}{@{}r@{}l@{}}
-    ot_{15}  = &\openrule{\{1 \xrightarrow{l}_{C_1} 1\}, ~~\{\xrightarrow{hb_{115}}\}, ~~v_{15}=hb_{115}}
+    ot_{15}  = &\openrule{\{1 \xrightarrow{l}_{C_1} 1\}, ~~\{\xrightarrow{hb_{115}}_P\}, ~~v_{15}=hb_{115}}
     {\ostate{11} \xrightarrow{v_{15}} \ostate{11}}\\
@@
 % \newpage
-% \appendix
-
+\appendix{
+\section{LOTOS Running Example}
+\QIN{
+We choose the LOTOS formula $(\delta(arg)+P)>>(acc(v);Q)$, composing several operators of LOTOS language, as our running example for the open automaton computing algorithm.
+In past papers, we already have the encoding of LOTOS operators \cite{HMZ:PDP15,henrio:Forte2016}.
+In Fig.~\ref{schema:lotos-pnet}, we show the encoding of the formula using the encoding of those operators.
+}
+
+\QIN{
+In fact, there are two encodings of the formula.
+The first one uses a controller with two states to indicate the position of the control point in the top level of pNet,  either in the left hand side $(\delta(arg)+P)$ or in the other side $(acc(v);Q)$.
+So it is ``state oriented''.
+Each side of the formula is act as a subnet of the root pNet node.
+Three synchronization vectors are given for synchronizing the behavior of the subnets.
+The first vector, transmitting an action $a_1$ of P, can only occur if a1 is not a $\delta$, the vector concrete syntax is typically ``$< l, a_1 , \_ > -> a_1$'', in which ``$\_$'' means that the corresponding subnet is not involved in this synchronization.
+The second one composes the action from the subnets and gives out a synchronized action $\underline{\delta(x)}$, where the underlined action stands for an internal (already synchronized) action, that cannot be further synchronized at upper levels.
+Synchronized action is a straightforward generalization of the notion of internal actions, that will be convenient for observing internal events during model-checking.
+The second vector constraints that the transition occurs only when process P performs a $\delta(x)$ action, transferring the control to Q, and sending a value x at the same time.
+Process Q must be ready to ``accept'' this value through an acc(x) action.
+The last one acts similar with the the first one while it transmits the action $a_2$ of Q.
+These synchronization vectors make the pNet act as the Enable operator.
+}
+
+\QIN{
+The second encoding is ``data oriented'', meaning that the state of the node controller is encoded in the value of the pLTS state variable(s).
+Here we have a single state variable s0, initialized as 0.
+Its value is ``0'' when the control is on P, and ``1'' when the control is on Q.
+The transitions in the pLTS have the more general syntax: ``<action-expr> [guard] {sequence of assignments}''.
+Guards and assignments can only use the values of variables of their source state and values from input variables in the action expression; and a transition can only assign variables of its target state.
+}
+
+\QIN{
+Two subnets separately act as the choice and action prefix operator, in which there is a parameterized labelled transition system (pLTS) as a controller and a hole as the process.
+In the node PN2, there are two synchronization vectors present that action $\delta(x)$ or action from P will be transmitted to the upper level, only once and only one of them will be activated according to C2.
+Then the same behavior will be continued, presented by the other two synchronization vectors.
+The node PN3 also has its own synchronization vectors to make it act as the prefix operator.
+}
+
+\QIN{
+It should be easy to see that this pNet system encodes properly the behavioral semantics of the corresponding CCS expression.
+Remark that it is built in a systematic structural way, one pNet node encoding each CCS operator.
+And it is parameterized both at the level of actions variables (occurring within the con- trollers and the synchronization vectors), and at the level of process parameters (holes).
+}
+
+\begin{figure}[h]
+  \centerline{\includegraphics[width=10cm]{XFIG/LOTOS1.eps}}
+  \hspace{0.5cm}
+  \centerline{\includegraphics[width=10cm]{XFIG/LOTOS2.eps}}
+  \caption{Two pNet encodings for the LOTOS formula }  \label{schema:lotos-pnet}
+\end{figure}
+
+\begin{figure}[h]
+  \centerline{\includegraphics[width=7cm]{XFIG/LOTOSresult}}
+
+$\begin{array}{@{}r@{}l@{}}
+    ot_1  = &\openrule{\{0 \xrightarrow{l}_{C_1} 0, 0 \xrightarrow{\delta(x)}_{C_2} 1\}, ~~\{\xrightarrow{hb_{11}}_P\}, ~~hb_{11}=a_1 \!\land\! a_1\neq \delta(x) \!\land\! v_1=a_1}
+    {\ostate{000} \xrightarrow{v_1} \ostate{020}}\\
+  \end{array}$
+
+$\begin{array}{@{}r@{}l@{}}
+    ot_2  = &\openrule{\{0 \xrightarrow{\delta}_{C_1} 1, 0 \xrightarrow{delta(x)}_{C_2} 1, 0 \xrightarrow{acc(x)}_{C_3} 1\}, ~~v_2=\underline{\delta(x)}}
+    {\ostate{000} \xrightarrow{v_2} \ostate{111}}\\
+  \end{array}$
+
+$\begin{array}{@{}r@{}l@{}}
+    ot_3  = &\openrule{\{0 \xrightarrow{\delta}_{C_1} 1, 0 \xrightarrow{p}_{C_2} 2, 0 \xrightarrow{acc(x)}_{C_3} 1\}, ~~\{\xrightarrow{hb_{13}}_P\}, ~~hb_{13}=\delta(x) \!\land\!
+v_3=\underline{\delta(x)}}
+    {\ostate{000} \xrightarrow{v_3} \ostate{121}}\\
+  \end{array}$
+
+$\begin{array}{@{}r@{}l@{}}
+    ot_4  = &\openrule{\{0 \xrightarrow{l}_{C_1} 0, 2 \xrightarrow{p}_{C_2} 2\}, ~~\{\xrightarrow{hb_{14}}_P\}, ~~hb_{14}=a_1 \!\land\! a_1\neq \delta(x) \!\land\! v_4=a_1}
+    {\ostate{020} \xrightarrow{v_4} \ostate{020}}\\
+  \end{array}$
+
+$\begin{array}{@{}r@{}l@{}}
+    ot_5  = &\openrule{\{0 \xrightarrow{\delta}_{C_1} 1, 2 \xrightarrow{p}_{C_2} 2, 0 \xrightarrow{acc(x)}_{C_3} 1\}, ~~\{\xrightarrow{hb_{15}}_P\}, ~~hb_{15}=\delta(x) \!\land\!
+v_5=\underline{\delta(x)}}
+    {\ostate{020} \xrightarrow{v_5} \ostate{121}}\\
+  \end{array}$
+
+$\begin{array}{@{}r@{}l@{}}
+    ot_6  = &\openrule{\{1 \xrightarrow{r}_{C_1} 1, 1 \xrightarrow{q}_{C_3} 1\}, ~~\{\xrightarrow{hb_{16}}_Q\}, ~~hb_{16}=a_2 \!\land\! a_2\neq acc(x) \!\land\! v_6=a_2}
+    {\ostate{111} \xrightarrow{v_6} \ostate{111}}\\
+  \end{array}$
+
+  $\begin{array}{@{}r@{}l@{}}
+    ot_7  = &\openrule{\{1 \xrightarrow{r}_{C_1} 1, 1 \xrightarrow{q}_{C_3} 1\}, ~~\{\xrightarrow{hb_{17}}_Q\}, ~~hb_{17}=a_2 \!\land\! a_2\neq acc(x) \!\land\! v_7=a_2}
+    {\ostate{121} \xrightarrow{v_7} \ostate{121}}\\
+  \end{array}$
+
+\caption{The open automaton of the LOTOS formula ($\delta$(arg)+P)>>(acc(v);Q)}  \label{schema:lotos-result}
+\end{figure}
+}
 \end{document}

### 2017-04-20 2017-Xudong-SMT/submit-ICTAC2017.tex
Reduce the pages of the paper.
Main content simplified
1.remove the detail description of modification on the sketch in the head of the Section 5.
2.simplify the subsection "Management of assignments" remove the initialization of state variables.
3.in subsection "Interaction with Z3" simplify the detail, remove the time point declaring and translating the presentation.
4.in "Translating assignments into predicate terms" shorten the description, add an example about the translation.

@@
 
+\QIN{
+We choose the LOTOS formula P>>(acc(v);Q), composing several operators of LOTOS language.
+}
+
 \begin{figure}[h]
-
-  \includegraphics[width=6cm]{XFIG/Enable1.eps}
-%  \hspace{0.5cm}
-  \includegraphics[width=6cm]{XFIG/Enable2.eps}
-  \caption{Two pNet encodings for the Lotos Enable operator P>>Q }  \label{schema:enable-pnets}
-
+  \centerline{\includegraphics[width=8cm]{XFIG/LOTOSFormula.eps}}
+  \caption{pNet encodings for the LOTOS formula}  \label{schema:lotos-pnet}
 \end{figure}
@@
 
-\TODO{To be re-written}
-
-In fact we give two encodings of this operator: the first one is
-``state oriented'', in the sense that the controller has two states,
-indicating where the control point is in the P>>Q process expression,
-either in P or in Q. The transition between these occurs when process
-P performs a $\delta(x)$ action, transferring the control to Q, and
-sending a value $x$ at the same time. Process Q must be ready to
-``accept'' this value through an $acc(x)$ action. The controller C1,
-and the 3 synchronization vectors of the Enable1 pNet should be easy
-to understand. Note 
-that the first vector, transmitting an action $a1$ of P, can only
-occur if $a1$ is not a $\delta$.
-
-The second encoding is ``data oriented'', meaning that the state of
-the node controller is encoded in the value of the pLTS state
-variable(s). Here we have a single state variable $s_0$, initialized
-as $0$. Its value is ``0'' when the control is on P, and ``1'' when the
-control is on Q. The transitions in the pLTS have the more general
-syntax: ``<action-expr> [guard] \{sequence of assignments\}''. Guards
-and assignments can only use the values of variables of their source
-state and values from input variables in the action expression; and a
-transition can only assign variables of its target state. 
-The second vector of the node ``Enable2'' also shows a
-$\underline{\delta(y_2)}$ result action, where the underlined action
-stands for an internal (already synchronized) action, that cannot be
-further synchronized at upper levels. This is a straightforward
- generalization of the notion of internal actions, that will be
-convenient for observing internal events during model-checking.
+\QIN{
+In Fig.~\ref{schema:lotos-pnet}, we show the encoding of the formula using the encoding.
+}
+
+\TODO{To be re-written[DONE]}
+
+\QIN{
+There are two styles of encodings used in the formula encoding.
+The first style is ``data oriented'', meaning that the state of the node controller, here is the pLTS C1, is encoded in the value of the pLTS state variable(s).
+Here we have a single state variable s0, initialized as 0.
+Its value is ``0'' when the control is on P, and ``1'' when the control is on Q.
+The second one uses a controller with two states to indicate the position of the control point in the right side of the formula $(acc(v);Q)$.
+So it is ``state oriented''.
+That is how we show prefix operator in PN2.
+}
+\QIN{
+The transitions in the pLTS have the more general syntax: ``<action-expr> [guard] {sequence of assignments}''.
+Guards and assignments can only use the values of variables of their source state and values from input variables in the action expression; and a transition can only assign variables of its target state.
+}
+
+\QIN{
+Each side of the formula is separately act as a hole $P$ and a sub-pNet PN2.
+Three synchronization vectors are given for synchronizing the behavior of the subnets to make the pNet act as the Enable operator..
+The first vector, transmitting an action $a_1$ of P, can only occur if a1 is not a $\delta$, the vector concrete syntax is typically ``$< l, a_1 , \_ > -> a_1$'', in which ``$\_$'' means that the corresponding subnet is not involved in this synchronization.
+The second one composes the action from the subnets and gives out a synchronized action $\underline{\delta(x)}$, where the underlined action stands for an internal (already synchronized) action, that cannot be further synchronized at upper levels.
+Synchronized action is a straightforward generalization of the notion of internal actions, that will be convenient for observing internal events during model-checking.
+The second vector constraints that the transition occurs only when process $P$ performs a $\delta(x)$ action, transferring the control to $Q$, and sending a value $x$ at the same time.
+This value must be ``accepted''  through an $acc(x)$ action before $Q$ taking the control.
+The last one acts similar with the the first one, it transmits the action $a_2$ of Q.
+}
+
+\QIN{
+The sub-pNet PN2 also have two synchronization vectors to make it act as the behavior of Prefix operator.
+}
+
+\QIN{
+It should be easy to see that this pNet system encodes properly the behavioral semantics of the corresponding CCS expression.
+Remark that it is built in a systematic structural way, one pNet node encoding each CCS operator.
+And it is parameterized both at the level of actions variables (occurring within the controllers and the synchronization vectors), and at the level of process parameters (holes).
+}
 
@@
 
-The preceding definition relies on the auxiliary functions below:
+%The preceding definition relies on the auxiliary functions below:
 
@@
   matching. May be we could remove it from here, but it will not gain
-  much...}
-
-\begin{definition}[Sorts, Holes, Leaves of pNets]
-  \begin{itemize}
-  \item The sort of a pNet is its signature, i.e. the set of actions it can
-perform. In the definition of sorts, we do not need to distinguish
-input variables (that specify the dataflow within LTSs), so for
-computing LTS sorts, we use a substitution operator\footnote{$\subst{y_k\gets x_k}^{k\in K}$ is the parallel substitution 
-operation.} to remove the
-\emph{input marker} of variables. Formally:
-\[
-\begin{array}{l}
-\Sort(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{x \gets ?x| 
-x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
-		J}\rangle} s'\in \to \} \\ \Sort(\mylangle
-\set{\pNet}, \set{\symb{S}}, \set{\symb{SV}}\myrangle) =\{\alpha'_k |\, \alpha_j^{j\in J_k}\to\alpha'_k\in\set{\symb{SV}}\}
-\end{array}
-\]
-
-\item
-The set of holes of a pNet is defined inductively; the sets of holes
-in a pNet node and its subnets are all disjoint:
-  \[\begin{array}{l}
-\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset \\
-\Holes(\mylangle \pNet_i^{i\in I}\!,S_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) =J\cup{\displaystyle \bigcup_{i\in I}\Holes(\pNet_i)}\\
-\forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
-\forall i_1,i_2\in I.\,i_1\neq i_2\Rightarrow  \Holes(\pNet_{i_1})\cap\Holes(\pNet_{i_2})=\emptyset
-\end{array}\]
-\item
-The set of leaves of a pNet is the set of all pLTSs occurring in the structure, defined inductively as:
-\[\begin{array}{l}
-\Leaves(\mylangle S,s_0, \to\myrangle) \!=\! \{ \mylangle S,s_0, \to\myrangle \}\\
-\Leaves(\mylangle \pNet_i^{i\in I}\!,S_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \bigcup_{i\in I}\Leaves(\pNet_i)}
-\end{array}\]
-\end{itemize}
-\end{definition}
-
-A pNet $Q$ is \emph{closed} if it has no hole: $\Holes(Q)=\emptyset$; else it
-is said to be \emph{open}.
+  much...[DONE]}
+
+%\begin{definition}[Sorts, Holes, Leaves of pNets]
+%  \begin{itemize}
+%  \item The sort of a pNet is its signature, i.e. the set of actions it can
+%perform. In the definition of sorts, we do not need to distinguish
+%input variables (that specify the dataflow within LTSs), so for
+%computing LTS sorts, we use a substitution operator\footnote{$\subst{y_k\gets x_k}^{k\in K}$ is the parallel substitution 
+%operation.} to remove the
+%\emph{input marker} of variables. Formally:
+%\[
+%\begin{array}{l}
+%\Sort(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{x \gets ?x| 
+%x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
+%		J}\rangle} s'\in \to \} \\ \Sort(\mylangle
+%\set{\pNet}, \set{\symb{S}}, \set{\symb{SV}}\myrangle) =\{\alpha'_k |\, \alpha_j^{j\in J_k}\to\alpha'_k\in\set{\symb{SV}}\}
+%\end{array}
+%\]
+%
+%\item
+%The set of holes of a pNet is defined inductively; the sets of holes
+%in a pNet node and its subnets are all disjoint:
+%  \[\begin{array}{l}
+%\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset \\
+%\Holes(\mylangle \pNet_i^{i\in I}\!,S_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) =J\cup{\displaystyle \bigcup_{i\in I}\Holes(\pNet_i)}\\
+%\forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
+%\forall i_1,i_2\in I.\,i_1\neq i_2\Rightarrow  \Holes(\pNet_{i_1})\cap\Holes(\pNet_{i_2})=\emptyset
+%\end{array}\]
+%\item
+%The set of leaves of a pNet is the set of all pLTSs occurring in the structure, defined inductively as:
+%\[\begin{array}{l}
+%\Leaves(\mylangle S,s_0, \to\myrangle) \!=\! \{ \mylangle S,s_0, \to\myrangle \}\\
+%\Leaves(\mylangle \pNet_i^{i\in I}\!,S_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \bigcup_{i\in I}\Leaves(\pNet_i)}
+%\end{array}\]
+%\end{itemize}
+%\end{definition}
+%
+%A pNet $Q$ is \emph{closed} if it has no hole: $\Holes(Q)=\emptyset$; else it
+%is said to be \emph{open}.
 
@@
 
+\QIN{[ change the example OT here ]}
 \begin{example}\emph{An open-transition.}
-  \label{OT:ccs-composed}
+  \label{OT:lotos-composed}
 \TODO{: change for an OT of new Lotos example, may be only one or two
-  of them ?}
-The \texttt{CCS} pNet of Fig.
-\ref{schema:ccs-pnets} has 2 controllers and 2 holes.
-We show its full open Automaton in section \ref{section:full-result}, it has 16 open transitions.
-We detail 3 of them here:
+  of them ?[DONE]}
+The \texttt{LOTOS} pNet of Fig.
+\ref{schema:lotos-pnet} has 1 controller and 1 hole.
+We show its full open Automaton in section \ref{section:full-result}, it has 5 open transitions.
+We detail 1 of them here:
 
  \smallskip
- $  OT_1  = \openrule{
-                       0 \xrightarrow{a}_{C_1} 1 ~~
-                       0 \xrightarrow{b}_{C_2} 1  ~~
-                       \{\}               ~~
-                 [ a\neq l \land b\neq r \land a=?ch(v) \land b=!ch(v) ]              
-                      }
-     {\ostate{00} \xrightarrow{\underline{\tau}} \ostate{11}}$
-
- $ OT_3  = \openrule{
-                       0 \xrightarrow{a}_{C_1} 1 ~~
-                       \{\}               ~~
-                 [ a\neq l  ]              
-                      }
-     {\ostate{10} \xrightarrow{a} \ostate{10}} $
-
-$  OT_{11}  = \openrule{
-                          1 \xrightarrow{l}_{C_1} 1 ~~
-                       0 \xrightarrow{b}_{C_2} 1 ~~
-                       \{ \xrightarrow{hb_P}_{P} \}               ~~
-                 [ a\neq l \land b\neq r \land hb_P=?ch(v) \land b=!ch(v) ]              
-                      }
-     {\ostate{10} \xrightarrow{\tau} \ostate{11}}
-  $
+ $ ot_2  = \openrule{
+                       \{0 \xrightarrow{\delta}_{C_1} 0, 0 \xrightarrow{acc(x)}_{C_2} 1\}, ~~
+                       \{\xrightarrow{hb_{12}}_P\}, ~~ 
+                        [s_0=0 \!\land\! hb_{12}=\delta(x)], ~~ 
+                       \{s_0 \xleftarrow{} 1\}     
+                      }
+     {\ostate{00} \xrightarrow{\underline{\delta(x)}} \ostate{01}}$
 \end{example}
 
-The first open transitions listed, $OT_1$ and $OT_3$, only involve
-possible actions from the prefix operators, respectively communication
-between the two prefixes, if actions $a$ and $b$ are matching emit and
-receive actions on the same channel; or simple propagation of action
-$a$ from the left prefix, with no special constraint other than being
-different from the local $l$ action of pLTS $C_1$.
-
-Remark the structured states in the conclusion of these rules: both
-start in state $\ostate{00}$, where both $C_1$ and $C_2$ are in their
-initial states. They end in different structured states, because in
-$OT_1$ both pLTS chage states, meaning that the control has gone
-respectively to processes $P$ and $Q$, consuming actions $A$ and $B$,
-while in $OT_3$ only $C_1$ has moved.
-
-The last open transition $OT_{11}$ starts in state $\ostate{10}$, with
-control at $P$ on the left, and action $b$ on the right. So these two
-can communicate, e.g. here if $b$ is an emission, and the action of hole
-$P$ is the matching reception.
+%The first open transitions listed, $OT_1$ and $OT_3$, only involve
+%possible actions from the prefix operators, respectively communication
+%between the two prefixes, if actions $a$ and $b$ are matching emit and
+%receive actions on the same channel; or simple propagation of action
+%$a$ from the left prefix, with no special constraint other than being
+%different from the local $l$ action of pLTS $C_1$.
+%
+%Remark the structured states in the conclusion of these rules: both
+%start in state $\ostate{00}$, where both $C_1$ and $C_2$ are in their
+%initial states. They end in different structured states, because in
+%$OT_1$ both pLTS chage states, meaning that the control has gone
+%respectively to processes $P$ and $Q$, consuming actions $A$ and $B$,
+%while in $OT_3$ only $C_1$ has moved.
+%
+%The last open transition $OT_{11}$ starts in state $\ostate{10}$, with
+%control at $P$ on the left, and action $b$ on the right. So these two
+%can communicate, e.g. here if $b$ is an emission, and the action of hole
+%$P$ is the matching reception.
+
+\QIN{
+The open transition $ot_2$ involve the possible actions from the process $P$ and prefix operator $(acc(x);Q$.
+The hole behavior $hb_{12}$ must be the exit action $\delta(x)$, if $(acc(x);Q$ can capture the same value $x$.
+}
+
+\QIN{
+Remark the structured states in the conclusion of these rules: both of them start in state $\ostate{00}$, where both $C_1$ and $C_2$ are in their initial states.
+They end in different structured states, because in $ot_2$ both pLTS conduct transitions, showing that the control has gone from processes $P$ to $(acc(x);Q$, consuming actions $\delta(x)$ and $acc(x)$.
+}
 
@@
 %
+%\begin{figure}[tb]
+%\begin{mathpar}
+%  \small
+%  \inferrule
+%    {\inferrule
+%      {
+%          \inferrule
+%              {1 \xrightarrow {l}_{C_1} 1}
+%              {C_1
+%                \models
+%                \openrule
+%                      {1 \xrightarrow{l}_{C_1} 1}
+%                      {\ostate{1}\xrightarrow{1}\ostate{1}}
+%              }
+%        }
+%        {\textrm{P}
+%          \models
+%            \openrule{
+%              1 \xrightarrow {l}_{C_1} 1,\,
+%              \{\xrightarrow{b_P}_P\},\, b_P\neq l}
+%                      {\ostate{1}\xrightarrow{b_P}\ostate{1}}
+%        }\\
+%%      \sm{fresh}v         \\
+%      \inferrule%*[right={L_1}]
+%        {
+%          \inferrule
+%              {0 \xrightarrow{b}_{C_2} 1}
+%              {C_4
+%                \models
+%                \openrule
+%                      {0 \xrightarrow{b}_{C_2} 0,\, b\neq r}
+%                      {\ostate{0}\xrightarrow{b}\ostate{1}}
+%              }
+%        }
+%        {
+%          \textrm{b:Q}\models
+%              \openrule
+%                  { 0 \xrightarrow {b}_{C_2} 1,\, \ b\neq r}
+%                  {\ostate{0}\xrightarrow{b}\ostate{1}}
+%        }   
+%    }
+%    {
+%     \textrm{PN1}
+%     \models
+%        \openrule{
+%                       1 \xrightarrow{l}_{C_1} 1 ~~
+%                       0 \xrightarrow{b}_{C_2} 1 ~~
+%                       \{ \xrightarrow{b_P}_{P} \}               ~~
+%                 [ a\neq l \land b\neq r \land b_P=?ch(v) \land b=!ch(v) ]              
+%                      }
+%     {\ostate{10} \xrightarrow{\tau} \ostate{11}}
+%      }\vspace{-4ex}
+%\end{mathpar}
+%  \caption{Proof of  $OT_{11}$ (with interaction of processes $P$ and action $b$) for ``a.P||b.Q''}
+%  \label{usingrules:OT11}
+%\end{figure}
+
 \begin{figure}[tb]
@@
   \inferrule
-    {\inferrule
     {
           \inferrule
-              {1 \xrightarrow {l}_{C_1} 1}
+              {0 \xrightarrow {\delta}_{C_1} 0 ~~
+               [ s_0=0 ]
+              }
               {C_1
@@
                 \openrule
-                      {1 \xrightarrow{l}_{C_1} 1}
-                      {\ostate{1}\xrightarrow{1}\ostate{1}}
-              }
-        }
-        {\textrm{a:P}
-          \models
-            \openrule{
-              1 \xrightarrow {l}_{C_1} 1,\,
-              \{\xrightarrow{b_P}_P\},\, b_P\neq l}
-                      {\ostate{1}\xrightarrow{b_P}\ostate{1}}
-        }\\
-%      \sm{fresh}v         \\
-      \inferrule%*[right={L_1}]
+                      {0 \xrightarrow{\delta}_{C_1} 0 ~~
+                       [ s_0=0 ] ~~
+                       \{ s_0 \leftarrow 1\}
+                      }
+                      {\ostate{0}\xrightarrow{\delta}\ostate{0}}
+              }
+	\\
+      \inferrule
         {
           \inferrule
-              {0 \xrightarrow{b}_{C_2} 1}
-              {C_4
+              {0 \xrightarrow{acc(x)}_{C_2} 1}
+              {C_2
                 \models
                 \openrule
-                      {0 \xrightarrow{b}_{C_2} 0,\, b\neq r}
-                      {\ostate{0}\xrightarrow{b}\ostate{1}}
+                      {0 \xrightarrow{acc(x)}_{C_2} 1}
+                      {\ostate{0}\xrightarrow{acc(x)}\ostate{1}}
               }
@@
         {
-          \textrm{b:Q}\models
+          \textrm{acc(x);Q}\models
               \openrule
-                  { 0 \xrightarrow {b}_{C_2} 1,\, \ b\neq r}
-                  {\ostate{0}\xrightarrow{b}\ostate{1}}
+                  { 0 \xrightarrow {acc(x)}_{C_2} 1}
+                  {\ostate{0}\xrightarrow{acc(x)}\ostate{1}}
         }   
@@
         \openrule{
-                       1 \xrightarrow{l}_{C_1} 1 ~~
-                       0 \xrightarrow{b}_{C_2} 1 ~~
-                       \{ \xrightarrow{b_P}_{P} \}               ~~
-                 [ a\neq l \land b\neq r \land b_P=?ch(v) \land b=!ch(v) ]              
-                      }
-     {\ostate{10} \xrightarrow{\tau} \ostate{11}}
+                        0 \xrightarrow{\delta}_{C_1} 0, 0 \xrightarrow{acc(x)}_{C_2} 1 ~~
+                       \{\xrightarrow{hb_{12}}_P\} ~~ 
+                        [s_0=0 \!\land\! hb_{12}=\delta(x)] ~~ 
+                       \{s_0 \xleftarrow{} 1\}           
+                      }
+     {\ostate{00} \xrightarrow{\tau} \ostate{01}}
       }\vspace{-4ex}
 \end{mathpar}
-  \caption{Proof of  $OT_{11}$ (with interaction of processes $P$ and action $b$) for ``a.P||b.Q''}
-  \label{usingrules:OT11}
+  \caption{Proof of  $ot_{2}$ (with interaction of processes $P$ and action $acc(x)$) for ``P>>(acc(x);Q)''}
+  \label{usingrules:ot2}
 \end{figure}
 
-\TODO{Change the example...?}
+\TODO{Change the example...?[DONE]}
 \begin{example} \emph{Using the operational rules to compute
     open-transitions}
-  In Fig. \ref{usingrules:OT11} we show the deduction tree used to construct and prove the 
-  open transition $OT_{11}$ of \texttt{CCS} (see example page
-  \pageref{OT:ccs-composed}).
+  In Fig. \ref{usingrules:ot2} we show the deduction tree used to construct and prove the 
+  open transition $ot_{2}$ of \texttt{LOTOS}.
+%(see example page \pageref{OT:ccs-composed}).
 %  \TODO{Eric: change for a deduction tree of CCS expression}
-The proof tree uses TR1 twice, for the $l$ transition of $C_1$ and for the
-  $b$ transition of $C_2$, then uses an action $b_P$ of hole $P$, and
-  combines the results using the second vector of the PN2 sub-pNet, and
-  the third vector of the top node. This yields a final $\tau$
-  transition. The deduction tree in the figure shows how the
-  predicates are generated in this process.
+%  The proof tree uses TR1 twice, for the $l$ transition of $C_1$ and for the
+%  $b$ transition of $C_2$, then uses an action $b_P$ of hole $P$, and
+%  combines the results using the second vector of the PN2 sub-pNet, and
+%  the third vector of the top node. This yields a final $\tau$
+%  transition. The deduction tree in the figure shows how the
+%  predicates are generated in this process.
 
 \end{example}
+
+\QIN{
+The proof tree uses TR1 twice, for the $\delta$ transition of $C_1$ and for the $acc(x)$ transition of $C_2$, then uses an action $b_{12}$ of hole $P$, and combines the results using the first vector of the PN2 sub-pNet, and the second vector of the top node according to TR2.
+This yields a final $\underline{\delta(x)}$ transition.
+The deduction tree in the figure shows how the predicates are generated in this process.
+}
 
@@
 action expressions and the data in their parameters is left open in
-the pNet formalisation.
+the pNet formalization.
 
@@
 \begin{itemize}
-	\item Sorts: Constants sets of the algebra, types of the data
+	\item Sorts: Constants sets of the algebra or types of the data
           and actions. 
@@
         \item Constants: The satisfiability solver need to know which
-          actions in the pLTS behaviors are constants (like the $l$,
-          $r$ local actions of the controllers in the CCS example). So
-          for a given pNet system, the Action sort will include all
+          actions in the pLTS behaviors are constants (like the $l$, $\delta$, 
+          $r$ of the controllers in running example). 
+          For a given pNet system, a sort $Action$ will include all
           these constants.
@@
 \paragraph{Sorts}
-Ownership of the variables and constants in a pNet acting as actions
-or data is probably various. Sorts are represented by their name. The
-sort of actions is built by the constant actions. Sorts here act as
-sets of actions for pNet, pLTS or 
-holes. There \emph{must} be one sort for actions, and eventually
-several others for the types of data parameters. Sorts for integer
-and boolean are implicitly declared.
-
-\QIN{
-In the CCS example, we have a sort for actions called $Action$:
-}
-
-\[ Action = \{ l, r\} \]
+\QIN{
+Sorts are represented by a given name, showing the ownership of the variables and constants. The
+sort of actions is built by the constant actions. There \emph{must} be one sort for actions, and eventually
+several others for the types of data parameters. In the LOTOS example, we have the $Action$ sort:
+}
+\[ Action = \{ l, \delta, r, p, q, acc \} \]
+
+In every presentation, sorts for integer and boolean are implicitly declared.
 
 \paragraph{Operators}
-We need introduce operators for building expressions, of both action
-and data sorts, when encoding the 
-algebra into pNets. So that is needed to know about the input and
-output of the operators used in the expressions from those
-algebra. The input and output should belong to the sorts of the
-pNet. When there are $k$ sorts in this pNet, the structure of a
-$n$-ary operator is vector as $< Sort_{i_1}, ... , Sort_{i_n} >
-\rightarrow Sort_j , i_1 , ... , i_n, j \in [0..k] $.
-
-\QIN{For instance, in our CCS running example, there is the action expression $!ch(v)$ using an operator $!$ presenting the ``$EMIT$'' action in CCS.
-We only use a sort called $Action$ to involve all the constant actions or action expressions in pNets and other parameters such as channel $ch$ or variable $v$ are all integers.
-So here we treat $EMIT$ as a binary operator with the format like:
-}
-
- \[ < Int, Int > \rightarrow Action . \]
-
- \paragraph{Implementation of the expression meta-model}
- \TODO{maybe we could remove this paragraph (and the figure)}
-The VerCors platform uses Ecore and EMF to define the structure of
-both pNets and actions algebras. There exists a predefined set of
-action and data expressions classes, including boolean, integer and
-action expressions, with predefined variables, literal (constants),
-and operators. Operators can be categorized into unary, binary and
-N-ary operators.
-The original version of VerCors did not allow to extend these classes,
-we have modified its architecture so that a user can extend them,
-defining more elements for his specific algebra.
-
-In Fig~\ref{schema:expression-pnets}, we show the Expression class we
-improved, including extensions for CCS and LOTOS.
+%We need introduce operators for building expressions, of both action
+%and data sorts, when encoding the 
+%algebra into pNets. So that is needed to know about the input and
+%output of the operators used in the expressions from those
+%algebra. The input and output should belong to the sorts of the
+%pNet. When there are $k$ sorts in this pNet, the structure of a
+%$n$-ary operator is vector as $< Sort_{i_1}, ... , Sort_{i_n} >
+%\rightarrow Sort_j , i_1 , ... , i_n, j \in [0..k] $.
+\QIN{
+We need introduce operators for building expressions, either action expressions or predicate terms, when encoding the algebra into pNets.
+The operators here are treated as functions, with the sorts of the pNet acting as the types of their input and output.
+}
+
+\QIN{For instance, in our LOTOS running example, we use a function ``$VOID$'' action to construct the action expression $\delta(x)$ and $acc(x)$.
+We can define the operator as a binary operator with the format like:
+}
+
+ \[VOID: \quad  < Action, Int > \rightarrow Action . \]
 
@@
 
-\begin{figure}[t]
-  \includegraphics[width=\linewidth]{XFIG/Expression}
-  \caption{The architecture of Expression class}  \label{schema:expression-pnets}
-\end{figure}
+%\paragraph{Implementation of the expression meta-model}
+% \TODO{maybe we could remove this paragraph (and the figure)}
+%The VerCors platform uses Ecore and EMF to define the structure of
+%both pNets and actions algebras. There exists a predefined set of
+%action and data expressions classes, including boolean, integer and
+%action expressions, with predefined variables, literal (constants),
+%and operators. Operators can be categorized into unary, binary and
+%N-ary operators.
+%The original version of VerCors did not allow to extend these classes,
+%we have modified its architecture so that a user can extend them,
+%defining more elements for his specific algebra.
+%
+%In Fig~\ref{schema:expression-pnets}, we show the Expression class we
+%improved, including extensions for CCS and LOTOS.
+%
+%\begin{figure}[t]
+%  \includegraphics[width=\linewidth]{XFIG/Expression}
+%  \caption{The architecture of Expression class}  \label{schema:expression-pnets}
+%\end{figure}
 
@@
 implementing the sketch showed before. However, we made some
-modifications due to implementation choices:
-\begin{itemize}
-  \item Steps 2a-2b are merged, applying Tr2 from the
-premisses OTs from subnets to generate OTs without
-explicitely constructing the deduction tree.
-  \item We define a general naming schema for implementing the fresh 
-and clone functions with more structure than a simple global name
-generator. It ensures unicity, but builds names
-readable enough for debugging purpose.
-  \item Besides that, we also have designed a management of state variables and
-    assignments throughout the whole computation.
-%%   \item Satisfiability check is done only at
-%% top level of the open-transition construction. An alternative would be
-%% to submit the satisfiability check to the SMT solver at each level of
-%% the hierarchical OT construction, potentially reducing the overall number of
-%% combinations. But the submission to the SMT engine is costly, and more
-%% complexity analysis is required before deciding if this would be
-%% worthwhile. 
-\end{itemize}
-
-In the following sections, we detail:
-\begin{itemize}
-\item The structure of fresh variable names.
-\item The details of the implementation for step 2a-2b, refined into:
-  \subitem combining all possibilities of subnets activity/inactivity,
-  \subitem matching each combination with synchronization vectors.
-\item Management of local variables of pLTSs.
-\item Pruning unsatisfiable OTs using the Z3 SMT solver.
-\end{itemize}
+modifications due to implementation choices.
+%:
+%\begin{itemize}
+%  \item Steps 2a-2b are merged, applying Tr2 from the
+%premisses OTs from subnets to generate OTs without
+%explicitely constructing the deduction tree.
+%  \item We define a general naming schema for implementing the fresh 
+%and clone functions with more structure than a simple global name
+%generator. It ensures unicity, but builds names
+%readable enough for debugging purpose.
+%  \item Besides that, we also have designed a management of state variables and
+%    assignments throughout the whole computation.
+%%%   \item Satisfiability check is done only at
+%%% top level of the open-transition construction. An alternative would be
+%%% to submit the satisfiability check to the SMT solver at each level of
+%%% the hierarchical OT construction, potentially reducing the overall number of
+%%% combinations. But the submission to the SMT engine is costly, and more
+%%% complexity analysis is required before deciding if this would be
+%%% worthwhile. 
+%\end{itemize}
+%
+%In the following sections, we detail:
+%\begin{itemize}
+%\item The structure of fresh variable names.
+%\item The details of the implementation for step 2a-2b, refined into:
+%  \subitem combining all possibilities of subnets activity/inactivity,
+%  \subitem matching each combination with synchronization vectors.
+%\item Management of local variables of pLTSs.
+%\item Pruning unsatisfiable OTs using the Z3 SMT solver.
+%\end{itemize}
 
@@
 
+%The variables in each synchronization vector are considered local, so
+%does the variables of an open transition such as its hole behaviors
+%and its result action. So we want rename the variables to make them
+%unique on every occurrence of a vector. Similarly, the name given to
+%the hole behaviors for each hole or the result action for each open
+%transition must be distinct. At the same time, we also hope them still
+%readable. Here we rename the variables with a regular format using the fresh function.
+
+\QIN{
 The variables in each synchronization vector are considered local, so
-does the variables of an open transition such as its hole behaviors
-and its result action. So we want rename the variables to make them
-unique on every occurrence of a vector. Similarly, the name given to
-the hole behaviors for each hole or the result action for each open
-transition must be distinct. At the same time, we also hope them still
-readable. Here we have defined a structure for the name of the fresh
-variables, the variables renamed with a regular format by the function
-fresh(). 
-\TODO{Could try to reduce the text, but give a couple examples ?}
+does the variables of an open transition, such as its hole behaviors
+and its result action. We want all the variables unique on every occurrence of them. 
+%Similarly, the name given to the hole behaviors for each hole or the result action for each open transition must be distinct. 
+At the same time, we also hope them still
+readable. Here we rename the variables with a regular format using the fresh function.
+}
+\TODO{Could try to reduce the text, but give a couple examples ?[DONE]}
 
@@
    \item[$\bullet$] $prefix$ is a default internal name for the variable. So far the internal name can be  sva (SV action), ra (result action), hb (hole behavior).
-   \item[$\bullet$] $tree\ index$ is the index of the node in the tree-like structure of the pNet.
+   \item[$\bullet$] $tree\ index$ is the index of the node containing the variable in the tree-like structure of the pNet.
    \item[$\bullet$] $counter$ is the current value of the corresponding counter.
@@
 
-$Prefix$ avoids the confusion between variables from different structures with the same name by attaching the type of the structure.
+%$Prefix$ avoids the confusion between variables from different structures with the same name by attaching the type of the structure.
 $Tree\ index$ is given to every node of the pNets to mention which node the variable belongs to as pNets has a tree-like structure.
@@
 
+\QIN{
+For example, in the running example, the first possible behavior of the hole, it doesn't have a name, only have the prefix ``hb''.
+The hole is the second subnets of the root node so its ``tree index'' is ``12''.
+The fresh variable name is ``$:hb:12:1$''.
+}
+
 \TODO{I have not yet been in details through the next section, but we
@@
 
-The predicate of the open transition is a conjunction of two parts
-every time applying Tr2. One part composes the predicate from the
+\begin{algorithm}
+\caption{Combining}
+\begin{algorithmic}[1]
+
+%\Require The list $TR$ of the open transition sets of the subnets. 
+%\Ensure The list of all the possible combinations of open transitions $L_C$.
+\State Initialise an empty combination list $L_C$;
+\State Extract a list of open transitions $L_{ot}$ from $TR$;
+\State Add $null$ to $L_{ot}$;
+\State Get the combinations $L'_C$ of the $TR$;
+\For{each $ot \in L_{ot}$}
+	\For{each $C' \in L'_C$}
+		\State Add $ot$ into $C'$ to get a new tuple $C$;
+		\State Add $C$ into $L_C$;
+	\EndFor
+\EndFor 
+\State \Return $L_C$;
+
+\end{algorithmic}  
+\end{algorithm}
+
+\QIN{
+Every time applying Tr2, we conduct combining and matching to generate predicates.
+The predicate of the open transition is a conjunction of two parts. The first part, which is the simpler one, composes the predicate from the
 subnets and the guard from transitions in sub-pLTS or synchronization
-vectors. The other part is the conjunction of equations generated
+vectors. The second part is the conjunction of equations generated
 during matching the subnets' behaviors with the synchronization
-vectors. Note that it is simple to collect required terms in the first
-part while in the second part we need to find out all the possible
-conjunction forms. We present here a algorithm divided in two
-step. Combining enumerates all the possible combinations of the
-working status. Matching synchronizes the subnets according to
-synchronization vectors to generate possible predicates.
+vectors. 
+}
+%Note that it is simple to collect required terms in the first
+%part while in the second part we need to find out all the possible
+%conjunction forms. We present here a algorithm divided in two
+%step. Combining enumerates all the possible combinations of the
+%working status. Matching synchronizes the subnets according to
+%synchronization vectors to generate possible predicates.
 
@@
 \paragraph{Combining}
-
-We first conduct combining. For each subnet, we enumerate all the
-possible cases of its working status. The result action of a pLTS or a
-pNet is the external action of the node shows the working status of
-it.
-
-For holes, their behavior is unspecified, it doesn't have an exact
-external presentation of action. We only give an action variable to each hole
-and treat it as hole behavior to suppose working status of the
-hole.
-% Here should have a constraint that this variable belongs to the sort of hole.
-In every case, the hole behaviors are unchanged, so we
-only make the combinations of subnets' open transitions.
-
-Algorithm 1 shows the combining algorithm for enumerating all the possible combinations of open transitions.
+%We first conduct combining. For each subnet, we enumerate all the
+%possible cases of its working status. The result action of a pLTS or a
+%pNet is the external action of the node shows the working status of
+%it.
+%
+%For holes, their behavior is unspecified, it doesn't have an exact
+%external presentation of action. We only give an action variable to each hole
+%and treat it as hole behavior to suppose working status of the
+%hole.
+%% Here should have a constraint that this variable belongs to the sort of hole.
+%In every case, the hole behaviors are unchanged, so we
+%only make the combinations of subnets' open transitions. 
+%
+%Algorithm 1 shows the combining algorithm for enumerating all the possible combinations of open transitions.
 The algorithm initializes an empty list $L_C$.
@@
 We get much more combinations after combining $ot$ from $L_{ot}$ with the partial result.
-
-\begin{algorithm}
-\caption{Combining}
-\begin{algorithmic}[1]
-
-\Require The list $TR$ of the open transition sets of the subnets. 
-\Ensure The list of all the possible combinations of open transitions $L_C$.
-\State Initialise an empty combination list $L_C$;
-\State Extract a list of open transitions $L_{ot}$ from $TR$;
-\State Add $null$ to $L_{ot}$;
-\State Get the combinations $L'_C$ of the $TR$;
-\For{each $ot \in L_{ot}$}
-	\For{each $C' \in L'_C$}
-		\State Add $ot$ into $C'$ to get a new tuple $C$;
-		\State Add $C$ into $L_C$;
-	\EndFor
-\EndFor 
-\State \Return $L_C$;
-
-\end{algorithmic}  
-\end{algorithm}
+\QIN{
+Algorithm 1 shows the combining algorithm for enumerating all the possible the possible working status combinations of subnets.
+Dealing with the list $TR$ containing several sets of open transitions from different subnets, the algorithm  chooses one of sets $L_{ot}$ and does combining on the remaining part of $TR$ recursively.
+Since there could exist the case that the subnet is not working, a $null$ is added into the $L_{ot}$ to represent it.
+We get much more combinations after combining $ot$ with the partial result.
+}
 
@@
 
-We now come to the matching using combinations from the previous step, together with hole behaviors and the result action, to match with the synchronization vectors.
-
-Algorithm 2 shows the algorithm matches combination $L_C$, hole
-behaviors $B$ with synchronization vectors $SV$. Remember variables
-inside a synchronization vector are consider local to the vector; so every time we choose a synchronization vector $sv$ from $SV$ for matching, we clone it and use the cloned one $sv'$.
+%We now come to the matching using combinations from the previous step, together with hole behaviors and the result action, to match with the synchronization vectors. 
+%
+%Algorithm 2 shows the algorithm matches combination $L_C$, hole
+%behaviors $B$ with synchronization vectors $SV$. Remember variables
+%inside a synchronization vector are consider local to the vector; so every time we choose a synchronization vector $sv$ from $SV$ for matching, we clone it and use the cloned one $sv'$.
 We use the definition declared before to construct all the possible predicates but the algorithm has not checked the correctness of these predicates.
-
-There is one mismatch case we can easily detect here, that is its
-working status:
-At any time an action $e_1$ matching with an element $e_2$ from
-synchronization vector, the pair $(e_1, e_2)$ must be checked: if both
-$e_1$ and $e_2$ are $null$ or $not\ null$, then it continues to
-generate a new term of predicate. Otherwise, it is intuitive that the
-working status coming from the subnet $e_1$ is different from what
-asked by the synchronization vector $e_2$, then this case is filtered
-out.
-
-Then we build the resulting open transition. Satisfiability of the
-predicate is not checked at this level, but only later, at the
-toplevel of the pNet.
+%
+%There is one mismatch case we can easily detect here, that is its
+%working status:
+%At any time an action $e_1$ matching with an element $e_2$ from
+%synchronization vector, the pair $(e_1, e_2)$ must be checked: if both
+%$e_1$ and $e_2$ are $null$ or $not\ null$, then it continues to
+%generate a new term of predicate. Otherwise, it is intuitive that the
+%working status coming from the subnet $e_1$ is different from what
+%asked by the synchronization vector $e_2$, then this case is filtered
+%out.
 
@@
 
-\Require 
-The combination of subnets' open transitions $L_C$;
-The behaviors of the holes $B$;
-The set of synchronization vectors $SV$.
-\Ensure 
-The list of all the possible open transitions generated $L_{ot}$.
+%\Require 
+%The combination of subnets' open transitions $L_C$;
+%The behaviors of the holes $B$;
+%The set of synchronization vectors $SV$.
+%\Ensure 
+%The list of all the possible open transitions generated $L_{ot}$.
 \State Initial an empty result list $L_{ot}$;
@@
 	\For{each $sv \in SV$}
-		\State Clone the $sv$, the result is denoted as $sv'$;
-		\State Generate the fresh result action v;
-		\State Combine $C, B, v$ as a new tuple $<C, B, v>$;
-		\For{each $e_1 \in <C, B, v> \&\& e_2 \in sv'$}
+		\State Clone the $sv$, the result is $sv'$;
+		\State Generate the fresh result action $ra$;
+		\State Combine $C, B, ra$ as a new vector $v$;
+		\For{each $(e_1 \in v )\&\& (e_2 \in sv')$}
 			\If{$(e_1\ is\ null\ \&\&\ e_2\ is\ not\ null)\ ||\ (e_1\ is\ not\ null\ \&\&\ e_2\ is\ null)$} 
@@
 			\Else 
-			\State Generate the term of predicate $t$;
-			\State Add $t$ into the $Pred$;
+			\State Add $(e_1 = e_2)$ into the $Pred$;
 			\EndIf
@@
 \end{algorithm}
+\QIN{
+Algorithm 2 shows the algorithm matches combination $L_C$, hole behaviors $B$ with synchronization vectors $SV$ according to the definition of the predicate declared before.
+We clone the $sv$ using the fresh function to generate a new $sv'$ with fresh variables.The mismatch on working status is easy to detect so we filter them in the algorithm through checking the matching elements $e_1$ and $e_2$.
+}
+
+Then we build the resulting open transition. Satisfiability of the
+predicate is not checked at this level, but only later, at the
+toplevel of the pNet.
 
 \subsection{Management of assignments}
-The pLTS contains some variables in each of its states (state
-variables), or just as global states of the pLTS (global variables).
-Both can be assigned in the pLTS transitions.
-The algorithm composing assignments from subnets is different from the
-generation of predicates. When applying Tr1, we just keep the
-assignments in the Post of the open transition. And when it comes to
-Tr2, Post is the union of the assignments propagate from the
-subnets. The assignments provide value of the variables in
-predicates.
-There is usually not only one assignment for a state variable as
-several incoming transitions of a state can perform different
-assignments on the same variable. The values of the
-variables are necessary for checking satisfiability of the open
-transitions together with predicates, miss of them may drop the
-unsatisfiable results. In order to avoid such mistakes, the algorithm
-manages the variables together with a list of all its possible assignments.
-
-We use a list of triples $<v,\ S, \ AssignRH>$ for each pLTS to record
-the information of both state and global variables of the pLTS where $v$ is the  variable in pLTS, $S$ is its owner state and $AssignRH$ is a list of expressions over other variables in the right hand side of assignments of $v$.
-The $S$ can be $null$ in the record triple, but it means the variable is global in the pLTS belonging to all the states instead of meaning it belongs to nothing.
-So it should be noted that the changing of the value of the global state variable every time a transition is conducted.
+%The pLTS contains some variables in each of its states (state
+%variables), or just as global states of the pLTS (global variables).
+%Both can be assigned in the pLTS transitions.
+%The algorithm composing assignments from subnets is different from the
+%generation of predicates. 
+%%When applying Tr1, we just keep the
+%%assignments in the Post of the open transition. And when it comes to
+%%Tr2, Post is the union of the assignments propagate from the
+%%subnets. 
+%The assignments provide value of the variables in
+%predicates. There is usually not only one assignment for a state variable as
+%several incoming transitions of a state can perform different
+%assignments on the same variable. The values of the
+%variables are necessary for checking satisfiability of the open
+%transitions together with predicates, miss of them may drop the
+%unsatisfiable results. In order to avoid such mistakes, the algorithm
+%manages the variables together with a list.
+%
+%The list we used contains triples $<v,\ S, \ AssignRH>$ set for each pLTS to record
+%the information of both state and global variables of the pLTS where $v$ is the variable in pLTS, $S$ is its owner state and $AssignRH$ is a list of expressions over other variables in the right hand side of assignments of $v$.
+The $S$ can be $null$ in the record triple, it means the variable is global in the pLTS belonging to all the states.
+%%So it should be noted that the changing of the value of the global state variable every time a transition is conducted.
 $AssignRH$ is the collection of all the possible expressions coming from the the right hand side of assignments.
 It keeps the information of the assignments for each variable.
-We update the list of record triples every time Tr1 is applied, adding the right side of the assignments into corresponding expression lists.
+%We update the list of record triples every time Tr1 is applied, adding the right side of the assignments into corresponding expression lists.
 So the list keeps the all the assignments in the pLTS.
 Then we can track all the possible value of the variables when computing open transitions.
-The initial value of the state variable is also seen as an assignment
-for that variable. We must give a initial value to the global state
-variable or there will be some problem in the start state. However, we
-sometimes don't give initial values to the state variables (except the
-global variables) as their initial values are decided by their first
-assignments. Checking whether each variable is initialized before
-being used is a separated problem, that should be done before starting
-our algorithm.
+%The initial value of the state variable is also seen as an assignment
+%for that variable. We must give a initial value to the global state
+%variable or there will be some problem in the start state. However, we
+%sometimes don't give initial values to the state variables (except the
+%global variables) as their initial values are decided by their first
+%assignments. Checking whether each variable is initialized before
+%being used is a separated problem, that should be done before starting
+%our algorithm.
+\QIN{
+There are some assignment on the variables in each of states of the pLTS (state variables), or just as global states of it (global variables).
+There is usually not only one assignment for a state variable, miss of them may drop the unsatisfiable results.
+In order to avoid such mistakes, the algorithm manages the variables together with a list for each pLTS.
+}
+
+\QIN{
+The list we used contains several triples <$v$, $S$, $AssignRH$> to record the information of both state and global variables of the pLTS, where $v$ is the variable in pLTS, $S$ is its owner state and $AssignRH$ is a list of expressions over other variables in the right hand side of assignments of $v$.
+It means the variable is global in the pLTS belonging to all the states, if $S$ is $null$.
+We update the list of record triples every time Tr1 is applied.
+Then we can track all the possible value of the variables when computing open transitions.
+}
 
@@
 
-We have used a brute-force method to generate all the possible open
-transitions in the open automaton. It obviously contains some of
-unsatisfiability in the open transitions. In
-Fig~\ref{schema:unsat-ot}, we display an unsatisfiable open transition
-from the result of the CCS running example. It shows the case that the
-top level transmits out the action from the PN2, formula $a.P$, as
-this time only PN2 is working and C1 is performing action $a$ when
-hole $P$ is also working. When matching this case against the second
-synchronization 
-vector of PN2, transmitting the behavior from hole $P$ to the higher
-level, is used while it is obviously violate the guard of the
-vector. So we can easily find the contradiction between the generated
-predicate term $ra:152:1=l \!\land\! a=:ra:152:1$ and the guard
-composed into the predicate $a \neq l$.
+%We have used a brute-force method to generate all the possible open
+%transitions in the open automaton. It obviously contains some of
+%unsatisfiability in the open transitions. In
+%Fig~\ref{schema:unsat-ot}, we display an unsatisfiable open transition
+%from the result of the CCS running example. It shows the case that the
+%top level transmits out the action from the PN2, formula $a.P$, as
+%this time only PN2 is working and C1 is performing action $a$ when
+%hole $P$ is also working. When matching this case against the second
+%synchronization 
+%vector of PN2, transmitting the behavior from hole $P$ to the higher
+%level, is used while it is obviously violate the guard of the
+%vector. So we can easily find the contradiction between the generated
+%predicate term $ra:152:1=l \!\land\! a=:ra:152:1$ and the guard
+%composed into the predicate $a \neq l$.
+
+\QIN{
+We have used a brute-force method to generate all the possible open transitions in the open automaton.
+It obviously contains some of unsatisfiability in the open transitions.
+In Fig~\ref{schema:unsat-ot}, we display an unsatisfiable open transition from the result of the LOTOS running example.
+It shows the case that the controller C1 want to move the control from $P$ to $(acc(x);Q)$, conducting a $\delta$ transition.
+However, the first synchronization vector is chosen, we can easily find the contradiction in the generated predicate term ``$:ra:11:1=l \!\land\!
+\delta=:ra:11:1$''.
+}
 
@@
 algorithm, in particular because it requires some symbolic computation
-on the action expressions and the predicates, and that this reasonning
+on the action expressions and the predicates, and that this reasoning
 may depend on the specific theory of the action algebra. 
@@
 \begin{figure}[t]
+%$\begin{array}{@{}r@{}l@{}}
+%%{s0---a-->s1},   {---:hb:15:2-->},   (:ra:15:2 = act:sva:1:3)/\(:ra:152:1 = l)/\(a = :ra:152:1)/\(l!= a)/\(:hb:15:2 = y:sva:15:2)/\(:ra:15:2 = y:sva:15:2)/\(y:sva:15:2 != l)/\(:ra:1:3 = act:sva:1:3)
+%    ot  = &\openrule{\{0 \xrightarrow{a} 1\}, ~~\{\xrightarrow{:hb:15:2}\}, ~~:ra:15:2=act:sva:1:3 \\
+%    \!\land\!:ra:152:1=l \!\land\! a=:ra:152:1 \!\land\! a \neq l \!\land\! :hb:15:2 = y:sva:15:2 \\
+%    \!\land\! :ra:15:2 = y:sva:15:2  \!\land\! y:sva:15:2 \neq l \!\land\! :ra:1:3 = act:sva:1:3}
+%    {\ostate{00} \xrightarrow{:ra:1:3} \ostate{10}}\\
+%  \end{array}$
+%\caption{One of the unsatisfiable open transitions in CCS running example}  \label{schema:unsat-ot}
+%\end{figure}
+
+%{s0---delta-->s0},   {---:hb_P:12:1-->},   (:ra:11:1=l)/\(delta=:ra:11:1)/\(var_s0=0)/\(:hb_P:12:1=a1:sva_SV0:1:1)/\(:ra:1:1=a1:sva_SV0:1:1)/\(a1:sva_SV0:1:1!=delta(x)),   {var_s0 := 1}
 $\begin{array}{@{}r@{}l@{}}
-%{s0---a-->s1},   {---:hb:15:2-->},   (:ra:15:2 = act:sva:1:3)/\(:ra:152:1 = l)/\(a = :ra:152:1)/\(l!= a)/\(:hb:15:2 = y:sva:15:2)/\(:ra:15:2 = y:sva:15:2)/\(y:sva:15:2 != l)/\(:ra:1:3 = act:sva:1:3)
-    ot  = &\openrule{\{0 \xrightarrow{a} 1\}, ~~\{\xrightarrow{:hb:15:2}\}, ~~:ra:15:2=act:sva:1:3 \\
-    \!\land\!:ra:152:1=l \!\land\! a=:ra:152:1 \!\land\! a \neq l \!\land\! :hb:15:2 = y:sva:15:2 \\
-    \!\land\! :ra:15:2 = y:sva:15:2  \!\land\! y:sva:15:2 \neq l \!\land\! :ra:1:3 = act:sva:1:3}
-    {\ostate{00} \xrightarrow{:ra:1:3} \ostate{10}}\\
+    ot  = &\openrule{\{0 \xrightarrow{\delta} 0\}, ~~\{\xrightarrow{:hb:12:1}\}, ~~:ra:11:1=l \!\land\! \delta=:ra:11:1 \!\land\! s0=0 \\
+     \!\land\! :hb:12:1=a1:sva:1:1 \!\land\! :ra:1:1=a1:sva:1:1 \!\land\! a1:sva:1:1 \neq \delta(x), ~~\{s0 \leftarrow 1\}}
+    {\ostate{00} \xrightarrow{:ra:1:1} \ostate{00}}\\
   \end{array}$
-\caption{One of the unsatisfiable open transitions in CCS running example}  \label{schema:unsat-ot}
+\caption{One of the unsatisfiable open transitions in LOTOS running example}  \label{schema:unsat-ot}
 \end{figure}
@@
 \begin{figure}[t]
-  \centerline{\includegraphics[width=10cm]{XFIG/SMTLIB1}}
+  \centerline{\includegraphics[width=10cm]{XFIG/SMTLIB2}}
   \caption{The input of the Z3 solver in SMT-LIB language and the output result}  \label{schema:smt-lib}
@@
 \begin{figure}[t]
-  \includegraphics[width=\linewidth]{XFIG/Interaction}
+  \centerline{\includegraphics[width=10cm]{XFIG/Interaction}}
   \caption{The architecture of the interaction between pNet API and Z3}  \label{schema:interaction}
@@
 %\TODO{1. example input of Z3 in SMT-LIB.[DONE] 2. software architecture.[DONE]}
-There are several ways to interact with the Z3 solver. 
-It is possible to use Z3 interactively using the SMT-LIB
-(Python-based) language. From inside our algorithm code, 
+%There are several ways to interact with the Z3 solver. 
+%It is possible to use Z3 interactively using the SMT-LIB
+%(Python-based) language. 
+From inside our algorithm code, 
 we implement the dynamic interaction between the pNet API and Z3
@@
 result before.
-The input starts with the declaration of the CCS action algebra types
+The input starts with the declaration of the LOTOS action algebra types
 and constructors.
-Some $datatypes$ are declared to input the sorts of the CCS example, here we only declare one $datatypes$ named $Action$ to involve all the constant actions.
+
+\QIN{
+Generally, some $datatypes$ are declared to input the sorts, while here we only declare one $datatypes$ named $Action$ to involve all the constant actions.
 The $Int$ and $Bool$ are already existed in Z3.
@@
 The variables contained in the predicate are declared first, then the terms of predicate are inputed as $assertions$ one by one.
-In the output, "(not and)" shows Z3 have found out the contradiction in the predicate and the result "unsat" is just what we expected.
-
-\TODO{edit the figure to make it smaller in height}
-
-We present the architecture of the interaction with Z3 in
-Fig~\ref{schema:interaction}.
-For each OT generated at the toplevel of a pNet, the predicate must be
-submitted for satisfiability check to Z3. For that we need to
-translate into Z3 (Java-API) syntax, both the elements of the action
-algebra, and the predicates itself, including the encoding of the
-variable assignments (the Post part).
-
-The $presentation$ of the action algebra
-is declared at the beginning of the algorithm as the $sorts$ and the
-$operators$ will be used throughout the whole algorithm. It is
-translated into $datatypes$ and $functions$ then submitted to the Z3
-at the same time.
+The result "unsat" in the output is just what we expected.
+}
+
+\TODO{edit the figure to make it smaller in height [DONE]}
+
+%We present the architecture of the interaction with Z3 in
+%Fig~\ref{schema:interaction}.
+%For each OT generated at the toplevel of a pNet, the predicate must be
+%submitted for satisfiability check to Z3. For that we need to
+%translate into Z3 (Java-API) syntax, both the elements of the action
+%algebra, and the predicates itself, including the encoding of the
+%variable assignments (the Post part).
+%
+%The $presentation$ of the action algebra
+%is declared at the beginning of the algorithm as the $sorts$ and the
+%$operators$ will be used throughout the whole algorithm. It is
+%translated into $datatypes$ and $functions$ then submitted to the Z3
+%at the same time.
 Each candidate predicate will then be translated into $assertions$ before submitted to Z3 after the algorithm computing out all the possible open transitions, they act as intermediate results there.
 Together with the $datatypes$ and $functions$, the $assertions$ are used to check the satisfiability of the predicate in Z3.
+\QIN{
+We present the architecture of the interaction with Z3 in Fig~\ref{schema:interaction}.
+For each OT generated at the top level of a pNet, the predicate must be submitted for satisfiability check to Z3.
+For that we need to translate the $presentation$, the predicates and the variable assignments (the Post part) into Z3 (Java-API) syntax.
+The $presentation$ and the predicates are translated separately.
+}
 
@@
 \QIN{
-So when we declare the operator EMIT we illustrated in section 4.1, it will be just declared together with the constants.
-}
-
- Although in Fig~\ref{schema:smt-lib} we have not declared $functions$, they should be exactly declared if there are new $operators$ declared in the $presentation$.
-The input type of the $function$ can be $Int$, $Bool$ or the $datatypes$ declared all determined by the construct of the  $operators$ in the presentation.
-For example, we define a new operator to present the equation between two actions in CCS example $\text{EQUAL}$ in the format likes:
-
-\[< Action , Action > \rightarrow Bool .\]
-
-It will be translated into the Z3 statement:
-
-\[\text{(declare-fun\ EQUAL\ (Action\ Action)\ Bool) .}\]
+So when we declare the operator VOID we illustrated in section 4.1, it will be just declared together with the constants likes:
+}
+
+\[(VOID\ (action3\ Action)(data\ Int)) .\]
+
+\QIN{
+The $functions$ can also be declared independently, it usually applies to functions return integer or boolean, in the format likes:
+}
+
+\[(declare\text{-}fun\ VOID\ (Action\ Int)\ Action) .\]
+%Although in Fig~\ref{schema:smt-lib} we have not declared $functions$ outside of $datatypes$, there still exists $functions$ declared independently.
+The input and output types of the $function$ are also determined by the construct of the  $operators$ in the presentation.
+For example, we define a new operator to present the equation between two actions in LOTOS example $\text{EQUAL}$ in the format likes:
+%
+%\[EQUAL: \quad < Action , Action > \rightarrow Bool .\]
+%
+%It will be translated into the Z3 statement: 
+%
+%\[\text{(declare-fun\ EQUAL\ (Action\ Action)\ Bool) .}\]
 
@@
 
-The assignments are also taken into account when checking the
-satisfiability of the open transitions as they represent the value of
-the variables involved in an OT. In order to do that, we employs a
-translation from assignments into term of predicates. The assignments
-required to be translated are only those belong to the variables
-contain in the start states of the open transitions. The assignments
-are represented as equations between the variables and the expressions
-on the right side of assignment. For the assignments of the same
-variable, we do not figure out which state is the precursor of current
-state, we keep all these possible equations instead, and generate the
-disjunction of these equations. The state could always move to the
-target state if there exists one of the values of its variable
-satisfies the guard.
-%\TODO{It won't matter the variable of the next state
-%except that the right hand side expression contain its variables. This
-%is a problem left to be solved in our future work. WHICH PROBLEM ?}
-After that, for the assignments of the different variables, we generate a conjunction of them. This way we obtain a new term of the predicate involving assignments of the variables.
-
-\paragraph{checking satisfiability}
+%The assignments are also taken into account when checking the
+%satisfiability of the open transitions as they represent the value of
+%the variables involved in an OT. In order to do that, we employs a
+%translation from assignments into term of predicates. The assignments
+%required to be translated are only those belong to the variables
+%contain in the start states of the open transitions. The assignments
+%are represented as equations between the variables and the expressions
+%on the right side of assignment. For the assignments of the same
+%variable, we do not figure out which state is the precursor of current
+%state, we keep all these possible equations instead, and generate the
+%disjunction of these equations. The state could always move to the
+%target state if there exists one of the values of its variable
+%satisfies the guard.
+%%\TODO{It won't matter the variable of the next state
+%%except that the right hand side expression contain its variables. This
+%%is a problem left to be solved in our future work. WHICH PROBLEM ?}
+%After that, for the assignments of the different variables, we generate a conjunction of them. This way we obtain a new term of the predicate involving assignments of the variables.
+\QIN{
+The assignments are also treated as a term of predicates when checking the satisfiability.
+Here we need conduct some translations, such as $\{s_0 \leftarrow 1\}$ in \ref{section:op-semantics}, we translate it into an equation $s_0=1$.
+Then for the assignments of the same variable, we do not figure out which state is the precursor of current state, we keep all these possible equations instead, and generate the disjunction of these equations.
+Correspondingly, we generate a conjunction for the assignments from the different variables.
+In this way, we obtain a new term of the predicate.
+}
+
+\paragraph{Checking satisfiability}
 
@@
 
-\[\text{(declare-const\ a\ Action) .}\]
+\[\text{(declare-const\ |:ra:1:1|\ Action) .}\]
 
@@
 
-\[(:ra:152:1 = l) \land (a = :ra:152:1) \land (l \neq a) .\]
-
-from which we generate the following three assertions:
-
-\[\text{(assert\ (=\ |:ra:152:1|\ l))}\ \ \ \text{(assert\ (=\ a\ |:ra:152:1|))}\ \ \ \text{(assert\ (not\ (=\ a\ l)))}\]
+\[(:ra:11:1=l)\land(delta=:ra:11:1) .\]
+
+from which we generate the following two assertions:
+
+\[(assert\ (=\ |:ra:11:1|\ l))\ \ \ (assert\ (=\ delta\ |:ra:11:1|))\]
 
@@
 
-We get the final result after pruning all the unsatisfiable open
-transitions, that is 2/3 of the intermediate results; the resulting open
-automaton is shown in Fig.~\ref{schema:ccs-result}, we have drawn
-manually the open automaton obtained as the final result generated by
-algorithm.
-The $ot_1$ represents the
-value-passing between $a.P$ and $b.Q$ and they are synchronized then
-give out an silent action $\tau$, process $P$ and $Q$ should not work
-in this case. The $ot_3$ and $ot_5$ represent another possible path to
-execute $a.P||b.Q$, action $a$ and $b$ are finished in sequence
-instead of synchronizing, they are just transmitted out as the
-external action. The behavior of the processes, presented as holes $P$
-and $Q$ in this pNet, is uncertain, we only know the sort $Action$ for
-them. So the action from $P$ might be synchronized with the action $b$
-that is what $ot_9$ presents or be directly transmitted to the
-external as the $ot_7$ shows. And we can see more cases of the
-interaction between these two processes in the open transitions starting at
-the state $11$, synchronizing two actions like $ot_{13}$ or directly
-transmitting like $ot_{15}$.
-
-To sum up, from the pNet encoding CCS formula inputed by the user we
-generate the open transitions and prune the unsatisfiability
-automatically. The final result open transitions represent all the
-possible movements of the CCS example.
+\QIN{
+We get the final result after pruning all the unsatisfiable open transitions and only 5 results left; the resulting open automaton is shown in Fig.
+~\ref{schema:lotos-result}, we have drawn manually the open automaton obtained as the final result generated by algorithm.
+}
+
+\QIN{The $ot_1$ shows that only the actions of the process $P$ could be transmitted out before the value $x$ being captured which is represented by the $ot_2$.
+The other 3 open transitions shows the behaviors of the process $Q$ while the $ot_3$ and $ot_4$ won't be performed as the controller has already set the value $s_0$ to 1 in the previous action.
+}
+
+\QIN{
+To sum up, from the pNet encoding LOTOS formula inputed by the user we generate the open transitions and prune the unsatisfiability automatically.
+The final result open transitions represent all the possible movements of the LOTOS example.
+They can exactly construct the open automaton for the given example.
+}
 
 \begin{figure}[h]
-  \centerline{\includegraphics[width=7cm]{XFIG/CCSresult}}
+  \centerline{\includegraphics[width=5cm]{XFIG/LOTOSresult}}
 
 $\begin{array}{@{}r@{}l@{}}
-    ot_1  = &\openrule{\{0 \xrightarrow{a}_{C_1} 1, 0 \xrightarrow{b}_{C_2} 1\}, ~~a=!ch_{11}(v_{11}) \!\land\! b=?ch_{11}(v_{11}) \!\land\! a\neq l \!\land\! b\neq r\!\land\! v_1=\tau}
-    {\ostate{00} \xrightarrow{v_1} \ostate{11}}\\
+    ot_1  = &\openrule{\{0 \xrightarrow{l}_{C_1} 0\}, ~~\{\xrightarrow{hb_{11}}_P\}, ~~[s_0=0 \!\land\! hb_{11}=a_1 \!\land\! a_1\neq \delta(x) \!\land\! v_1=hb_{11}]}
+    {\ostate{00} \xrightarrow{v_1} \ostate{00}}\\
   \end{array}$
 
-  \begin{minipage}{6cm}
 $\begin{array}{@{}r@{}l@{}}
-    ot_3  = &\openrule{\{0 \xrightarrow{a}_{C_1} 1\}, ~~a\neq l \!\land\! v_3=a}
-    {\ostate{00} \xrightarrow{v_3} \ostate{10}}\\
-    ot_5  = &\openrule{\{0 \xrightarrow{b}_{C_2} 1\}, ~~b\neq r \!\land\! v_5=b}
-    {\ostate{10} \xrightarrow{v_5} \ostate{11}}\\
+    ot_2  = &\openrule{\{0 \xrightarrow{\delta}_{C_1} 0, 0 \xrightarrow{acc(x)}_{C_2} 1\}, ~~\{\xrightarrow{hb_{12}}_P\}, ~~[s_0=0 \!\land\!
+hb_{12}=\delta(x) \!\land\!
+v_2=\underline{\delta(x)}], ~~\{s_0 \xleftarrow{} 1\}}
+    {\ostate{00} \xrightarrow{v_2} \ostate{01}}\\
   \end{array}$
-  \end{minipage}
-   \hspace{2mm}
-  \begin{minipage}{6cm}
+
 $\begin{array}{@{}r@{}l@{}}
-    ot_7  = &\openrule{\{1 \xrightarrow{l}_{C_1} 1\}, ~~\{\xrightarrow{hb_{17}}\}, ~~v_7=hb_{17}}
-    {\ostate{10} \xrightarrow{v_7} \ostate{10}}\\
+    ot_3  = &\openrule{\{0 \xrightarrow{l}_{C_1} 0\}, ~~\{\xrightarrow{hb_{13}}_P\}, ~~[s_0=0 \!\land\! hb_{13}=a_1 \!\land\! a_1\neq \delta(x) \!\land\! v_3=a_1]}
+    {\ostate{01} \xrightarrow{v_3} \ostate{01}}\\
   \end{array}$
-  \end{minipage}
 
 $\begin{array}{@{}r@{}l@{}}
-    ot_9  = &\openrule{\{0 \xrightarrow{b}_{C_2} 1\}, ~~\{\xrightarrow{hb_{19}}\}, ~~b=!ch_{19}(v_{19}) \!\land\! b\neq r \!\land\! hb_{19}=?ch_{19}(v_{19})\!\land\! v_9=\tau}
-    {\ostate{10} \xrightarrow{v_9} \ostate{11}}\\
+    ot_4  = &\openrule{\{0 \xrightarrow{\delta}_{C_1} 0, 1 \xrightarrow{acc(x)}_{C_2} 1\}, ~~\{\xrightarrow{hb_{14}}_P\}, ~~[s_0=0 \!\land\!
+hb_{14}=\delta(x) \!\land\!
+v_4=\underline{\delta(x)}], ~~\{s_0 \xleftarrow{} 1\}}
+    {\ostate{01} \xrightarrow{v_5} \ostate{01}}\\
   \end{array}$
@@
   $\begin{array}{@{}r@{}l@{}}
-    ot_{13}  = &\openrule{\{1 \xrightarrow{l}_{C_1} 1, 1 \xrightarrow{r}_{C_2} 1\}, ~~\{\xrightarrow{hb_{113}}, \xrightarrow{hb_{213}}\}, ~~hb_{113}= !ch_{113}(v_{113}) \!\land\!
-hb_{213}=?ch_{113}(v_{113}) \!\land\!
-v_{13}=\tau}
-    {\ostate{11} \xrightarrow{v_{13}} \ostate{11}}\\
+    ot_5  = &\openrule{\{0 \xrightarrow{r}_{C_1} 0, 1 \xrightarrow{q}_{C_2} 1\}, ~~\{\xrightarrow{hb_{15}}_Q\}, ~~[s_0=1 \!\land\! hb_{15}=a_2 \!\land\! a_2\neq acc(x) \!\land\! v_5=a_2]}
+    {\ostate{01} \xrightarrow{v_5} \ostate{01}}\\
   \end{array}$
 
-$\begin{array}{@{}r@{}l@{}}
-    ot_{15}  = &\openrule{\{1 \xrightarrow{l}_{C_1} 1\}, ~~\{\xrightarrow{hb_{115}}\}, ~~v_{15}=hb_{115}}
-    {\ostate{11} \xrightarrow{v_{15}} \ostate{11}}\\
-  \end{array}$
-
-\caption{The open automaton of the CCS formula a.P||b.Q (a part of open transitions is shown)}  \label{schema:ccs-result}
+\caption{The open automaton of the LOTOS formula}  \label{schema:lotos-result}
 \end{figure}
@@
 automatically. The open automaton successfully presents all the
-possible movements of the CCS expression.
+possible movements of the LOTOS expression.
 
@@
 predicates.
-We may also try other automatic theorem provers, depending on th
-estructure of the proofs we need.
+We may also try other automatic theorem provers, depending on the structure of the proofs we need.
 
@@
 step we may want instead to define and implement an algorithm fo
-rchecking that a given equivalence relation between open automata
-states is indeed a FH-Bisimulation. Finding automaticaly a
+r checking that a given equivalence relation between open automata
+states is indeed a FH-Bisimulation. Finding automatically a
 bisimulation relation or the most general bisimulation will be more
@@
 different structure, strong bisimulation will be too strong a notion,
-and that we will have to define proper notinos of weak equivalence or
+and that we will have to define proper notions of weak equivalence or
 refinements.
@@
 result that we showed in the bottom part of
-Fig.~\ref{schema:ccs-result} is not the one generated by the algorithm,
+Fig.~\ref{schema:lotos-result} is not the one generated by the algorithm,
 because it contains many intermediate
@@
 The result of the elimination will be simpler predicates, that can be
-successfuly compared (e.g. by Z3) within the bisimulation checking
+successfully compared (e.g. by Z3) within the bisimulation checking
 algorithm.

### 2017-04-20 2017-Xudong-SMT/submit-ICTAC2017.tex
small stuff...

@@
   matching. May be we could remove it from here, but it will not gain
-  much...[DONE]}
+  much...[DONE] --- Well, not really, because you have not chnaged the places where SORT is used, e.g.
+in definitions 2 and 3 one minimal solution is to add a sentence with a ref to Forte'16 --- but also you have removed the defs of Holes and Leaves, that we really use a lot !}
 
@@
 
-\QIN{[ change the example OT here ]}
+%\QIN{[ change the example OT here ]}
 \begin{example}\emph{An open-transition.}
   \label{OT:lotos-composed}
-\TODO{: change for an OT of new Lotos example, may be only one or two
-  of them ?[DONE]}
+
 The \texttt{LOTOS} pNet of Fig.
-\ref{schema:lotos-pnet} has 1 controller and 1 hole.
-We show its full open Automaton in section \ref{section:full-result}, it has 5 open transitions.
-We detail 1 of them here:
+\ref{schema:lotos-pnet} has 2 controllers and 2 holes.
+We will show its full open Automaton in section \ref{section:full-result}, it has 5 open transitions.
+We detail one of them here:
 
@@
 
-\QIN{
-The open transition $ot_2$ involve the possible actions from the process $P$ and prefix operator $(acc(x);Q$.
-The hole behavior $hb_{12}$ must be the exit action $\delta(x)$, if $(acc(x);Q$ can capture the same value $x$.
-}
-
-\QIN{
+The open transition $ot_2$ involves the possible actions from the process $P$ and prefix expression $acc(x);Q$.
+The hole behavior, represented by variable $hb_{12}$ must be equal to the exit action $\delta(x)$, and the accept event $acc(x)$ will capture the same value $x$.
+
 Remark the structured states in the conclusion of these rules: both of them start in state $\ostate{00}$, where both $C_1$ and $C_2$ are in their initial states.
 They end in different structured states, because in $ot_2$ both pLTS conduct transitions, showing that the control has gone from processes $P$ to $(acc(x);Q$, consuming actions $\delta(x)$ and $acc(x)$.
-}
+Controller $C_1$ has only one state, but its state variable $s_0$ has changed to 1.
 
@@
 
-\QIN{
-We have used a brute-force method to generate all the possible open transitions in the open automaton.
-It obviously contains some of unsatisfiability in the open transitions.
-In Fig~\ref{schema:unsat-ot}, we display an unsatisfiable open transition from the result of the LOTOS running example.
-It shows the case that the controller C1 want to move the control from $P$ to $(acc(x);Q)$, conducting a $\delta$ transition.
-However, the first synchronization vector is chosen, we can easily find the contradiction in the generated predicate term ``$:ra:11:1=l \!\land\!
-\delta=:ra:11:1$''.
-}
-
-To get a correct open
-automaton of the pNet, such unsatisfiable open transitions need to be
-eliminated. This is not easy to perform directly inside our
-algorithm, in particular because it requires some symbolic computation
-on the action expressions and the predicates, and that this reasoning
+We use a brute-force method to generate all the possible open
+transitions in the open automaton, using all possible combinations of
+synchronisation vectors. Naturally this builds open transtions where
+the predicates express uncompatible constraints. Even if having an
+unsatisfiable transition in the open automaton would not be incorrect,
+we want to check them for satisfiability, and reduce the number of
+transitions and states in the automaton.
+In Fig.~\ref{schema:unsat-ot}, we display an example of an
+unsatisfiable open transition 
+from the result of our example. It shows the case where
+the controller C1 wants to move the control from $P$ to $(acc(x);Q)$,
+conducting a $\delta$ transition. However, the first synchronization
+vector is chosen, we can easily find the contradiction in the
+generated predicate term ``$:ra:11:1=l \!\land\! \delta=:ra:11:1$''.
+
+Checking satisfiability requires some symbolic computation
+on the action expressions and the predicates, and this reasoning
 may depend on the specific theory of the action algebra. 
-We choose a SMT solver Z3 as the checker for the open
+We choose to use the SMT solver Z3 as the checker for the open
 transitions considering the predicates may contain the expression
@@
     ot  = &\openrule{\{0 \xrightarrow{\delta} 0\}, ~~\{\xrightarrow{:hb:12:1}\}, ~~:ra:11:1=l \!\land\! \delta=:ra:11:1 \!\land\! s0=0 \\
-     \!\land\! :hb:12:1=a1:sva:1:1 \!\land\! :ra:1:1=a1:sva:1:1 \!\land\! a1:sva:1:1 \neq \delta(x), ~~\{s0 \leftarrow 1\}}
+     \!\land\! \texttt{:hb:12:1}=\texttt{a1:sva:1:1} \!\land\! :ra:1:1=a1:sva:1:1 \!\land\! a1:sva:1:1 \neq \delta(x), ~~\{s0 \leftarrow 1\}}
     {\ostate{00} \xrightarrow{:ra:1:1} \ostate{00}}\\
@@
 \begin{figure}[t]
-  \centerline{\includegraphics[width=10cm]{XFIG/SMTLIB2}}
+  \centerline{\includegraphics[width=11cm]{XFIG/SMTLIB2}}
   \caption{The input of the Z3 solver in SMT-LIB language and the output result}  \label{schema:smt-lib}
@@
 %(Python-based) language. 
-From inside our algorithm code, 
-we implement the dynamic interaction between the pNet API and Z3
-solver through its JAVA API. But here we present the code in Z3 by
-SMT-LIB language instead of JAVA codes to make it easier to read. In
-Fig~\ref{schema:smt-lib}, we show the  input of the unsatisfiable
-result before.
-The input starts with the declaration of the LOTOS action algebra types
-and constructors.
+From inside our algorithm code, we submit satisfiability requests to
+Z3 using its JAVA API. In this article, to make the reading easier, we
+show the Z3 code fragments using its SMT-LIB input language. As an
+example in
+Fig~\ref{schema:smt-lib}, we show the input for checking the (unsatisfiable)
+transition of Fig.~\ref{schema:unsat-ot}.
+
+The input to Z3 contains the declaration of the LOTOS action algebra types
+and constructors, then the declaration of variables, and finaly the
+predicate to be checked, encoded as a set of assertions.
 
@@
 
-\TODO{edit the figure to make it smaller in height [DONE]}
+%\TODO{edit the figure to make it smaller in height [DONE]}
 
@@
 \QIN{
-We present the architecture of the interaction with Z3 in Fig~\ref{schema:interaction}.
-For each OT generated at the top level of a pNet, the predicate must be submitted for satisfiability check to Z3.
-For that we need to translate the $presentation$, the predicates and the variable assignments (the Post part) into Z3 (Java-API) syntax.
+We present the architecture of the interaction with Z3 in
+Fig~\ref{schema:interaction}. For each OT generated at the top level
+of a pNet, the predicate must be submitted for satisfiability check to
+Z3.
+For that we need to translate the algebra $presentation$, the predicates and the variable assignments (the Post part) into Z3 (Java-API) syntax.
 The $presentation$ and the predicates are translated separately.

### 2017-04-20 2017-Xudong-SMT/submit-ICTAC2017.tex
one more

@@
 \begin{itemize}
-\item We have refined the open automaton generation algorithm, to make
+\item \ERIC{We have refined the open automaton generation algorithm, to make
   it implementable, and we implemented a full working prototype, within the
-  VerCors platform. In the process, we had to improve slightly the
-  semantics rules, and to add features in the algorithm to deal with
-  management of variables and assignements.
-  \item We extended the meta-model of action expressions, and the
-    associated API, in the VerCors platform, to be able to manage
-    parameterisation over the action algebra operators.
+  VerCors platform. In the process, we had to improve significantly the
+  semantics rules, and add features in the algorithm to deal the full
+  model, including management of variables and assignements.}
+%  \item We extended the meta-model of action expressions, and the
+%    associated API, in the VerCors platform, to be able to manage
+%    parameterisation over the action algebra operators.
   \item We have implemented the interaction between our algorithm and the Z3
@@
     generated by the algorithm.
-    \item We validated the whole approach on several use-cases, taken
-      from two different process languages.
+    \item \ERIC{We validated the whole approach on a small use-case covering all
+      important features of the model.}
 \end{itemize}
@@
 \paragraph{Structure.}
-In \ref{section:examples} we present two simple examples that will be
-running examples to illustrate all parts of the paper. Then in the
+In \ref{section:examples} we present a simple example that will  illustrate all parts of the paper. Then in the
 background section
@@
 implementation within the Vercors platform, and shows the full result of
-the semantic computation on one of the running examples.
+the semantic computation on the running example.
 Finally we conclude and discuss perspectives in section
@@
 In this paper, we use a running example inspired from Lotos, to illustrate
-the main features of pNets and the manner we deal with them in the symbolic
+the main features of pNets and the way we deal with them in the symbolic
 semantics, and in the satifiability checking.
-
-\QIN{
-We choose the LOTOS formula P>>(acc(v);Q), composing several operators of LOTOS language.
-}
 
@@
   \centerline{\includegraphics[width=8cm]{XFIG/LOTOSFormula.eps}}
-  \caption{pNet encodings for the LOTOS formula}  \label{schema:lotos-pnet}
+  \caption{pNet encodings for the LOTOS expression}  \label{schema:lotos-pnet}
 \end{figure}
 
-This example is based on the Enable
-operator of the LOTOS language. For the readers not familiar with
+We choose the expression \texttt{P>>(accept(v);Q)}, that includes the
+Enable and Prefix 
+operators of the LOTOS language. For the readers not familiar with
 Lotos, the pNet encodings here should be sufficient to understand the
 Enable operator semantics.
-
-\QIN{
-In Fig.~\ref{schema:lotos-pnet}, we show the encoding of the formula using the encoding.
-}
-
-\TODO{To be re-written[DONE]}
-
-\QIN{
-There are two styles of encodings used in the formula encoding.
-The first style is ``data oriented'', meaning that the state of the node controller, here is the pLTS C1, is encoded in the value of the pLTS state variable(s).
-Here we have a single state variable s0, initialized as 0.
-Its value is ``0'' when the control is on P, and ``1'' when the control is on Q.
-The second one uses a controller with two states to indicate the position of the control point in the right side of the formula $(acc(v);Q)$.
-So it is ``state oriented''.
-That is how we show prefix operator in PN2.
-}
-\QIN{
-The transitions in the pLTS have the more general syntax: ``<action-expr> [guard] {sequence of assignments}''.
-Guards and assignments can only use the values of variables of their source state and values from input variables in the action expression; and a transition can only assign variables of its target state.
-}
-
-\QIN{
-Each side of the formula is separately act as a hole $P$ and a sub-pNet PN2.
-Three synchronization vectors are given for synchronizing the behavior of the subnets to make the pNet act as the Enable operator..
-The first vector, transmitting an action $a_1$ of P, can only occur if a1 is not a $\delta$, the vector concrete syntax is typically ``$< l, a_1 , \_ > -> a_1$'', in which ``$\_$'' means that the corresponding subnet is not involved in this synchronization.
-The second one composes the action from the subnets and gives out a synchronized action $\underline{\delta(x)}$, where the underlined action stands for an internal (already synchronized) action, that cannot be further synchronized at upper levels.
-Synchronized action is a straightforward generalization of the notion of internal actions, that will be convenient for observing internal events during model-checking.
-The second vector constraints that the transition occurs only when process $P$ performs a $\delta(x)$ action, transferring the control to $Q$, and sending a value $x$ at the same time.
-This value must be ``accepted''  through an $acc(x)$ action before $Q$ taking the control.
-The last one acts similar with the the first one, it transmits the action $a_2$ of Q.
-}
-
-\QIN{
-The sub-pNet PN2 also have two synchronization vectors to make it act as the behavior of Prefix operator.
-}
-
-\QIN{
-It should be easy to see that this pNet system encodes properly the behavioral semantics of the corresponding CCS expression.
-Remark that it is built in a systematic structural way, one pNet node encoding each CCS operator.
-And it is parameterized both at the level of actions variables (occurring within the controllers and the synchronization vectors), and at the level of process parameters (holes).
-}
+In Fig.~\ref{schema:lotos-pnet}, we show the encoding of the formula using our encoding.
+
+\ERIC{
+  This pNet is composed of: a toplevel node PN1 encoding the Enable
+  operator, with its ``controller'' C1; a ``hole'' representing the
+  process variable P; another node PN2 representing the Prefix
+  operator, with its controller C2, and its hole Q. Controllers are
+  labelled transition systems (pLTS) with state variables and value-passing
+  transitions, defining the dynamics of the operator semantics.}
+
+In order to show all features of the pNet model, we choose to use two
+styles of encodings used in the controllers.
+The most common style used in process calculi is ``state oriented'',
+we use it here for C2: it has two states to
+indicate the position of the control point in the right side of the
+Prefix expression $(acc(v);Q)$. The second one is
+``data oriented'': controler C1 has a single state, with a state
+variable s0 encoding the change of control point from left to right sub-net.
+The transitions in the pLTS have the more general syntax:
+``<action-expr> [guard] {sequence of assignments}''. Guards and
+assignments can only use the values of variables of their source state
+and values from input variables in the action expression; and a
+transition can only assign variables of its target state.
+
+Now look more specifically on the top pNet node PN1. In addition to
+its controller it has 2 sub-pNets, the hole P and the sub-pNet PN2.
+Three synchronization vectors are given for synchronizing the behavior
+of the subnets to make the pNet act as the Enable operator. The first
+vector, transmitting an action $a_1$ of P, can only occur if $a_1$ is not
+a $\delta$, the vector concrete syntax is typically ``$< l, a_1 , \_ >
+-> a_1$'', in which ``$\_$'' means that the corresponding subnet is
+not involved in this synchronization, and the ``l'' action is related
+to the corresponding transition of the controller C1.
+The second vector composes the
+action from the subnets and gives out a synchronized action
+$\underline{\delta(x)}$, where the underlined action stands for an
+internal (already synchronized) action, that cannot be further
+synchronized at upper levels. Synchronized action is a straightforward
+generalization of the notion of internal actions, that will be
+convenient for observing internal events during model-checking. The
+second vector constraints that the transition occurs only when process
+$P$ performs a $\delta(x)$ action, transferring the control to $Q$,
+and sending a value $x$ at the same time. This value must be
+``accepted''  through an $acc(x)$ action before $Q$ taking the
+control. The last one acts as the first one, but transmitting the
+action $a_2$ of Q.  
+Similarily the node PN2 has two synchronization vectors to encode
+the behavior of the Prefix operator.
+
+It should be easy to see that this pNet system encodes properly the
+behavioral semantics of the corresponding Lotos expression. Remark
+that it is built in a systematic structural way, one pNet node
+encoding each Lotos operator. It is parameterized both at the level of
+actions variables (occurring within the controllers and the
+synchronization vectors), and at the level of process parameters
+(holes).
 
@@
 
-\TODO{I have removed some of the technical stuff, adding referemces to Forte'16.
-  We will see if this is enough, and will have to check if this is coherent, and if we can remove more, but for ICTAC, we MUST keep enough formal stuff}
+% \TODO{I have removed some of the technical stuff, adding referemces to Forte'16.
+%  We will see if this is enough, and will have to check if this is coherent, and if we can remove more, but for ICTAC, we MUST keep enough formal stuff}
 
@@
 communications.
-\TODO{I removed the CCS input action stuff, check later if we need to
-  replace it here by something different about input action notation}.
+%\TODO{I removed the CCS input action stuff, check later if we need to
+%  replace it here by something different about input action notation}.
 
@@
 
+By lack of space, we have omitted here the formal (structural)
+definition of $Sorts$ (the 
+set of actions of a hole or a pNet), $Leaves$ and $Holes$ (all pLTSs
+(resp holes) in a pNet hierarchical system). These can be found in \cite{henrio:Forte2016}.
 %The preceding definition relies on the auxiliary functions below:
-
-\TODO{we do not use the Sort in the implementation of synch vector
-  matching. May be we could remove it from here, but it will not gain
-  much...[DONE] --- Well, not really, because you have not chnaged the places where SORT is used, e.g.
-in definitions 2 and 3 one minimal solution is to add a sentence with a ref to Forte'16 --- but also you have removed the defs of Holes and Leaves, that we really use a lot !}
 
@@
 
-The \texttt{LOTOS} pNet of Fig.
-\ref{schema:lotos-pnet} has 2 controllers and 2 holes.
-We will show its full open Automaton in section \ref{section:full-result}, it has 5 open transitions.
-We detail one of them here:
+The \texttt{LOTOS} pNet of Fig. \ref{schema:lotos-pnet} has 2
+controllers and 2 holes. We will show its full open Automaton in
+section \ref{section:full-result}. We detail one of its transition here:
 
@@
 
-Remark the structured states in the conclusion of these rules: both of them start in state $\ostate{00}$, where both $C_1$ and $C_2$ are in their initial states.
-They end in different structured states, because in $ot_2$ both pLTS conduct transitions, showing that the control has gone from processes $P$ to $(acc(x);Q$, consuming actions $\delta(x)$ and $acc(x)$.
-Controller $C_1$ has only one state, but its state variable $s_0$ has changed to 1.
+Remark the structured states in the conclusion of this rule, encoding
+the combination of state-spaces of the leaves: both of them start in
+state $\ostate{00}$, where both $C_1$ and $C_2$ are in their initial
+states. They end in different structured states, because in $ot_2$
+both pLTS conduct transitions, showing that the control has gone from
+processes $P$ to $(acc(x);Q$, consuming actions $\delta(x)$ and
+$acc(x)$. Controller $C_1$ has only one state, but its state variable
+$s_0$ has changed to 1.
 
@@
 When building an Open Automaton as the semantics of a pNet, its
-\emph{states}, and the from of the predicates in its
+\emph{states}, and the shape of the predicates in its
 \emph{transitions} have a specific structure:
@@
 
-\begin{figure}[tb]
-\begin{mathpar}
-  \small
-  \inferrule
-    {
-          \inferrule
-              {0 \xrightarrow {\delta}_{C_1} 0 ~~
-               [ s_0=0 ]
-              }
-              {C_1
-                \models
-                \openrule
-                      {0 \xrightarrow{\delta}_{C_1} 0 ~~
-                       [ s_0=0 ] ~~
-                       \{ s_0 \leftarrow 1\}
-                      }
-                      {\ostate{0}\xrightarrow{\delta}\ostate{0}}
-              }
-	\\
-      \inferrule
-        {
-          \inferrule
-              {0 \xrightarrow{acc(x)}_{C_2} 1}
-              {C_2
-                \models
-                \openrule
-                      {0 \xrightarrow{acc(x)}_{C_2} 1}
-                      {\ostate{0}\xrightarrow{acc(x)}\ostate{1}}
-              }
-        }
-        {
-          \textrm{acc(x);Q}\models
-              \openrule
-                  { 0 \xrightarrow {acc(x)}_{C_2} 1}
-                  {\ostate{0}\xrightarrow{acc(x)}\ostate{1}}
-        }   
-    }
-    {
-     \textrm{PN1}
-     \models
-        \openrule{
-                        0 \xrightarrow{\delta}_{C_1} 0, 0 \xrightarrow{acc(x)}_{C_2} 1 ~~
-                       \{\xrightarrow{hb_{12}}_P\} ~~ 
-                        [s_0=0 \!\land\! hb_{12}=\delta(x)] ~~ 
-                       \{s_0 \xleftarrow{} 1\}           
-                      }
-     {\ostate{00} \xrightarrow{\tau} \ostate{01}}
-      }\vspace{-4ex}
-\end{mathpar}
-  \caption{Proof of  $ot_{2}$ (with interaction of processes $P$ and action $acc(x)$) for ``P>>(acc(x);Q)''}
-  \label{usingrules:ot2}
-\end{figure}
-
-\TODO{Change the example...?[DONE]}
 \begin{example} \emph{Using the operational rules to compute
@@
 \end{example}
+
+\begin{figure}[h]
+\begin{mathpar}
+  \small
+  \inferrule
+    {
+          \inferrule
+              {0 \xrightarrow {\delta}_{C_1} 0 ~~
+               [ s_0=0 ]
+              }
+              {C_1
+                \models
+                \openrule
+                      {0 \xrightarrow{\delta}_{C_1} 0 ~~
+                       [ s_0=0 ] ~~
+                       \{ s_0 \leftarrow 1\}
+                      }
+                      {\ostate{0}\xrightarrow{\delta}\ostate{0}}
+              }
+	\\
+      \inferrule
+        {
+          \inferrule
+              {0 \xrightarrow{acc(x)}_{C_2} 1}
+              {C_2
+                \models
+                \openrule
+                      {0 \xrightarrow{acc(x)}_{C_2} 1}
+                      {\ostate{0}\xrightarrow{acc(x)}\ostate{1}}
+              }
+        }
+        {
+          \textrm{acc(x);Q}\models
+              \openrule
+                  { 0 \xrightarrow {acc(x)}_{C_2} 1}
+                  {\ostate{0}\xrightarrow{acc(x)}\ostate{1}}
+        }   
+    }
+    {
+     \textrm{PN1}
+     \models
+        \openrule{
+                        0 \xrightarrow{\delta}_{C_1} 0, 0 \xrightarrow{acc(x)}_{C_2} 1 ~~
+                       \{\xrightarrow{hb_{12}}_P\} ~~ 
+                        [s_0=0 \!\land\! hb_{12}=\delta(x)] ~~ 
+                       \{s_0 \xleftarrow{} 1\}           
+                      }
+     {\ostate{00} \xrightarrow{\tau} \ostate{01}}
+      }\vspace{-4ex}
+\end{mathpar}
+  \caption{Proof of  $ot_{2}$ (with interaction of processes $P$ and action $acc(x)$) for ``P>>(acc(x);Q)''}
+  \label{usingrules:ot2}
+\end{figure}
 
@@
 In this section we present an algorithm to construct the open
-automaton representing the behaviour of an open pNet, and we prove that
+automaton representing the behavior of an open pNet, and we prove that
 under reasonable conditions this automaton is finite.

### 2017-04-20 2017-Xudong-SMT/submit-ICTAC2017.tex
Change the font style of variables.
Add two new commands \OTvar and \OTland.

@@
 \newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
+\newcommand{\OTvar}{\texttt}
+\newcommand{\OTland}{\ \land\ }
 \definecolor{airforceblue}{rgb}{0.26, 0.44, 0.56}
@@
 }
-\[ Action = \{ l, \delta, r, p, q, acc \} \]
+\[\OTvar{Action = } \{ l, \delta, r, p, q, acc \} .\]
 
@@
 
- \[VOID: \quad  < Action, Int > \rightarrow Action . \]
+ \[\OTvar{VOID:}\OTvar{< Action, Int >} \rightarrow \OTvar{Action .} \]
 
@@
 %    ot  = &\openrule{\{0 \xrightarrow{a} 1\}, ~~\{\xrightarrow{:hb:15:2}\}, ~~:ra:15:2=act:sva:1:3 \\
-%    \!\land\!:ra:152:1=l \!\land\! a=:ra:152:1 \!\land\! a \neq l \!\land\! :hb:15:2 = y:sva:15:2 \\
-%    \!\land\! :ra:15:2 = y:sva:15:2  \!\land\! y:sva:15:2 \neq l \!\land\! :ra:1:3 = act:sva:1:3}
+%    \OTland:ra:152:1=l \OTland a=:ra:152:1 \OTland a \neq l \OTland :hb:15:2 = y:sva:15:2 \\
+%    \OTland :ra:15:2 = y:sva:15:2  \OTland y:sva:15:2 \neq l \OTland :ra:1:3 = act:sva:1:3}
 %    {\ostate{00} \xrightarrow{:ra:1:3} \ostate{10}}\\
@@
 $\begin{array}{@{}r@{}l@{}}
-    ot  = &\openrule{\{0 \xrightarrow{\delta} 0\}, ~~\{\xrightarrow{:hb:12:1}\}, ~~:ra:11:1=l \!\land\! \delta=:ra:11:1 \!\land\! s0=0 \\
-     \!\land\! \texttt{:hb:12:1}=\texttt{a1:sva:1:1} \!\land\! :ra:1:1=a1:sva:1:1 \!\land\! a1:sva:1:1 \neq \delta(x), ~~\{s0 \leftarrow 1\}}
-    {\ostate{00} \xrightarrow{:ra:1:1} \ostate{00}}\\
+    ot  = &\openrule{\{0 \xrightarrow{\delta} 0\}, ~~\{\xrightarrow{:hb:12:1}\}, ~~\OTvar{:ra:11:1}=l \OTland \delta=\OTvar{:ra:11:1} \OTland \OTvar{s0}=0 \\
+     \OTland \OTvar{:hb:12:1}=\OTvar{a1:sva:1:1} \OTland \OTvar{:ra:1:1}=\OTvar{a1:sva:1:1} \OTland \OTvar{a1:sva:1:1} \neq \delta(x), ~~\{\OTvar{s0} \leftarrow 1\}}
+    {\ostate{00} \xrightarrow{\OTvar{:ra:1:1}} \ostate{00}}\\
   \end{array}$
@@
 
-\[(VOID\ (action3\ Action)(data\ Int)) .\]
+\[\OTvar{(VOID\ (action3\ Action)(data\ Int)) .}\]
 
@@
 
-\[(declare\text{-}fun\ VOID\ (Action\ Int)\ Action) .\]
+\[\OTvar{(declare\text{-}fun\ VOID\ (Action\ Int)\ Action) .}\]
 %Although in Fig~\ref{schema:smt-lib} we have not declared $functions$ outside of $datatypes$, there still exists $functions$ declared independently.
@@
 
-\[\text{(declare-const\ |:ra:1:1|\ Action) .}\]
+\[\OTvar{(declare-const\ |:ra:1:1|\ Action) .}\]
 
@@
 
-\[(:ra:11:1=l)\land(delta=:ra:11:1) .\]
+\[\OTvar{(:ra:11:1=l)} \OTland \OTvar{(delta=:ra:11:1) .}\]
 
@@
 
-\[(assert\ (=\ |:ra:11:1|\ l))\ \ \ (assert\ (=\ delta\ |:ra:11:1|))\]
+\[\OTvar{(assert\ (=\ |:ra:11:1|\ l))\ \ \ (assert\ (=\ delta\ |:ra:11:1|)) .}\]
 

### 2017-04-20 2017-Xudong-SMT/submit-ICTAC2017.tex
till page 12

@@
 \paragraph{Structure.}
-In \ref{section:examples} we present a simple example that will  illustrate all parts of the paper. Then in the
-background section
+In section
 \ref{section:pnets} we give a description and a formal definition of
-the pNet model, as found in previous publications.
+the pNet model, as found in previous publications. Then in
+\ref{section:examples} we present a simple example that will
+illustrate the rest of the paper.
 Section \ref{section:op-semantics} recalls the operational semantics
@@
 \ref{section:conclusion}.
-
-\section{Running Examples}
-\label{section:examples}
-
-Several publications \cite{HMZ:PDP15,henrio:Forte2016} already have introduced
-many examples of pNets, encoding
-operators of various classical process algebras, or more complex
-synchronization structures in distributed or parallel languages.
-In this paper, we use a running example inspired from Lotos, to illustrate
-the main features of pNets and the way we deal with them in the symbolic
-semantics, and in the satifiability checking.
-
-\begin{figure}[h]
-  \centerline{\includegraphics[width=8cm]{XFIG/LOTOSFormula.eps}}
-  \caption{pNet encodings for the LOTOS expression}  \label{schema:lotos-pnet}
-\end{figure}
-
-We choose the expression \texttt{P>>(accept(v);Q)}, that includes the
-Enable and Prefix 
-operators of the LOTOS language. For the readers not familiar with
-Lotos, the pNet encodings here should be sufficient to understand the
-Enable operator semantics.
-In Fig.~\ref{schema:lotos-pnet}, we show the encoding of the formula using our encoding.
-
-\ERIC{
-  This pNet is composed of: a toplevel node PN1 encoding the Enable
-  operator, with its ``controller'' C1; a ``hole'' representing the
-  process variable P; another node PN2 representing the Prefix
-  operator, with its controller C2, and its hole Q. Controllers are
-  labelled transition systems (pLTS) with state variables and value-passing
-  transitions, defining the dynamics of the operator semantics.}
-
-In order to show all features of the pNet model, we choose to use two
-styles of encodings used in the controllers.
-The most common style used in process calculi is ``state oriented'',
-we use it here for C2: it has two states to
-indicate the position of the control point in the right side of the
-Prefix expression $(acc(v);Q)$. The second one is
-``data oriented'': controler C1 has a single state, with a state
-variable s0 encoding the change of control point from left to right sub-net.
-The transitions in the pLTS have the more general syntax:
-``<action-expr> [guard] {sequence of assignments}''. Guards and
-assignments can only use the values of variables of their source state
-and values from input variables in the action expression; and a
-transition can only assign variables of its target state.
-
-Now look more specifically on the top pNet node PN1. In addition to
-its controller it has 2 sub-pNets, the hole P and the sub-pNet PN2.
-Three synchronization vectors are given for synchronizing the behavior
-of the subnets to make the pNet act as the Enable operator. The first
-vector, transmitting an action $a_1$ of P, can only occur if $a_1$ is not
-a $\delta$, the vector concrete syntax is typically ``$< l, a_1 , \_ >
--> a_1$'', in which ``$\_$'' means that the corresponding subnet is
-not involved in this synchronization, and the ``l'' action is related
-to the corresponding transition of the controller C1.
-The second vector composes the
-action from the subnets and gives out a synchronized action
-$\underline{\delta(x)}$, where the underlined action stands for an
-internal (already synchronized) action, that cannot be further
-synchronized at upper levels. Synchronized action is a straightforward
-generalization of the notion of internal actions, that will be
-convenient for observing internal events during model-checking. The
-second vector constraints that the transition occurs only when process
-$P$ performs a $\delta(x)$ action, transferring the control to $Q$,
-and sending a value $x$ at the same time. This value must be
-``accepted''  through an $acc(x)$ action before $Q$ taking the
-control. The last one acts as the first one, but transmitting the
-action $a_2$ of Q.  
-Similarily the node PN2 has two synchronization vectors to encode
-the behavior of the Prefix operator.
-
-It should be easy to see that this pNet system encodes properly the
-behavioral semantics of the corresponding Lotos expression. Remark
-that it is built in a systematic structural way, one pNet node
-encoding each Lotos operator. It is parameterized both at the level of
-actions variables (occurring within the controllers and the
-synchronization vectors), and at the level of process parameters
-(holes).
 
@@
 
+\section{Running Example}
+\label{section:examples}
+
+Several publications \cite{HMZ:PDP15,henrio:Forte2016} already have introduced
+many examples of pNets, encoding
+operators of various classical process algebras, or more complex
+synchronization structures in distributed or parallel languages.
+In this paper, we use a running example inspired from Lotos, to illustrate
+the main features of pNets and the way we deal with them in the symbolic
+semantics, and in the satifiability checking.
+
+\begin{figure}[h]
+  \centerline{\includegraphics[width=8cm]{XFIG/LOTOSFormula.eps}}
+  \caption{pNet encodings for the LOTOS expression}  \label{schema:lotos-pnet}
+\end{figure}
+
+We choose the expression \texttt{P>>(acc(v);Q)}, that includes the
+Enable and Prefix 
+operators of the LOTOS language. For the readers not familiar with
+Lotos, the pNet encodings here should be sufficient to understand the
+Enable operator semantics.
+In Fig.~\ref{schema:lotos-pnet}, we show the encoding of the formula using pNets.
+
+  This pNet is composed of: a toplevel node PN1 encoding the Enable
+  operator, with its controller (pLTS) C1; a hole representing the
+  process variable P; another node PN2 representing the Prefix
+  operator, with its controller C2, and its hole Q.
+
+In order to show all features of the pNet model, we choose to use two
+styles of encodings in the controllers.
+The most common style used in process calculi is ``state oriented'',
+we use it here for C2: it has two states to
+indicate the position of the control point in the
+Prefix expression $(acc(v);Q)$. The second one is
+``data oriented'': controller C1 has a single state, with a state
+variable $s_0$ encoding the change of control point from the left to
+the right sub-net.
+%% The transitions in the pLTS have the more general syntax:
+%% ``<action-expr> [guard] {sequence of assignments}''. Guards and
+%% assignments can only use the values of variables of their source state
+%% and values from input variables in the action expression; and a
+%% transition can only assign variables of its target state.
+
+Now look more specifically on the top pNet node PN1. In addition to
+its controller it has 2 sub-pNets: the hole P and the sub-pNet PN2.
+Three synchronization vectors are defining the possible
+synchronisations between the actions of the subnets.
+ The first
+vector, transmitting an action $a_1$ of P, can only occur if $a_1$ is not
+a $\delta$, the vector concrete syntax is typically ``$< l, a_1 , \_ >
+-> a_1$'', in which ``$\_$'' means that the corresponding subnet is
+not involved in this synchronization, and the ``l'' action is related
+to the corresponding transition of the controller C1: this action is
+available only when the state variable $s_0$ is equal to 0.
+The second vector composes the
+actions from the subnets and gives out a synchronized action
+$\underline{\delta(x)}$, where the underlined action stands for an
+internal (already synchronized) action, that cannot be further
+synchronized at upper levels. Synchronized action is a straightforward
+generalization of the notion of internal actions, that will be
+convenient for observing internal events during model-checking. Here
+the transition occurs only when process
+$P$ performs a $\delta(x)$ action, transferring the control to $Q$,
+and sending a value $x$ at the same time. This value must be
+``accepted''  through an $acc(x)$ action before $Q$ takes the
+control. The last vector acts as the first one, but transmitting the
+action $a_2$ of Q.  
+Similarily the node PN2 has two synchronization vectors to encode
+the behavior of the Prefix operator.
+
+It should be easy to see that this pNet system encodes properly the
+behavioral semantics of the corresponding Lotos expression. Remark
+that it is built in a systematic structural way, one pNet node
+encoding each Lotos operator. It is parameterized both at the level of
+actions variables (occurring within the controllers and the
+synchronization vectors), and at the level of process parameters
+(holes).
+
 \section{Operational Semantics for Open pNets}
@@
 
-%\QIN{[ change the example OT here ]}
-\begin{example}\emph{An open-transition.}
-  \label{OT:lotos-composed}
-
-The \texttt{LOTOS} pNet of Fig. \ref{schema:lotos-pnet} has 2
-controllers and 2 holes. We will show its full open Automaton in
-section \ref{section:full-result}. We detail one of its transition here:
-
- \smallskip
- $ ot_2  = \openrule{
-                       \{0 \xrightarrow{\delta}_{C_1} 0, 0 \xrightarrow{acc(x)}_{C_2} 1\}, ~~
-                       \{\xrightarrow{hb_{12}}_P\}, ~~ 
-                        [s_0=0 \!\land\! hb_{12}=\delta(x)], ~~ 
-                       \{s_0 \xleftarrow{} 1\}     
-                      }
-     {\ostate{00} \xrightarrow{\underline{\delta(x)}} \ostate{01}}$
-\end{example}
-
-%The first open transitions listed, $OT_1$ and $OT_3$, only involve
-%possible actions from the prefix operators, respectively communication
-%between the two prefixes, if actions $a$ and $b$ are matching emit and
-%receive actions on the same channel; or simple propagation of action
-%$a$ from the left prefix, with no special constraint other than being
-%different from the local $l$ action of pLTS $C_1$.
-%
-%Remark the structured states in the conclusion of these rules: both
-%start in state $\ostate{00}$, where both $C_1$ and $C_2$ are in their
-%initial states. They end in different structured states, because in
-%$OT_1$ both pLTS chage states, meaning that the control has gone
-%respectively to processes $P$ and $Q$, consuming actions $A$ and $B$,
-%while in $OT_3$ only $C_1$ has moved.
-%
-%The last open transition $OT_{11}$ starts in state $\ostate{10}$, with
-%control at $P$ on the left, and action $b$ on the right. So these two
-%can communicate, e.g. here if $b$ is an emission, and the action of hole
-%$P$ is the matching reception.
-
-The open transition $ot_2$ involves the possible actions from the process $P$ and prefix expression $acc(x);Q$.
-The hole behavior, represented by variable $hb_{12}$ must be equal to the exit action $\delta(x)$, and the accept event $acc(x)$ will capture the same value $x$.
-
-Remark the structured states in the conclusion of this rule, encoding
-the combination of state-spaces of the leaves: both of them start in
-state $\ostate{00}$, where both $C_1$ and $C_2$ are in their initial
-states. They end in different structured states, because in $ot_2$
-both pLTS conduct transitions, showing that the control has gone from
-processes $P$ to $(acc(x);Q$, consuming actions $\delta(x)$ and
-$acc(x)$. Controller $C_1$ has only one state, but its state variable
-$s_0$ has changed to 1.
-
 \begin{definition}[Open automaton]
@@
 
-\begin{definition}[States of open pNets]\label{def-states}
+\paragraph{States of open pNets:}\label{def-states}
   A state of an open pNet is a tuple (not necessarily finite) of the
@@
 $InitState(p) = \triangleleft {{s_i}_0}^{i\in L}  \triangleright$.
-\end{definition}
 
@@
 
+%\QIN{[ change the example OT here ]}
+\begin{example}\emph{An open-transition.}
+  \label{OT:lotos-composed}
+
+The \texttt{LOTOS} pNet of Fig. \ref{schema:lotos-pnet} has 2
+controllers and 2 holes. We will show its full open Automaton in
+section \ref{section:full-result}. We give one of its transition here:
+
+ \smallskip
+ $ ot_2  = \openrule{
+                       \{0 \xrightarrow{\delta}_{C_1} 0, 0 \xrightarrow{acc(x)}_{C_2} 1\}, ~~
+                       \{\xrightarrow{hb_{12}}_P\}, ~~ 
+                        [s_0=0 \!\land\! hb_{12}=\delta(x)], ~~ 
+                       \{s_0 \xleftarrow{} 1\}     
+                      }
+     {\ostate{00} \xrightarrow{\underline{\delta(x)}} \ostate{01}}$
+\end{example}
+
+The open transition $ot_2$ involves the possible actions from the process $P$ and prefix expression $acc(x);Q$.
+The hole behavior, represented by variable $hb_{12}$ must be equal to the exit action $\delta(x)$, and the accept event $acc(x)$ will capture the same value $x$.
+
+Theh transition in the conclusion of this rule starts in
+state $\ostate{00}$, where both $C_1$ and $C_2$ are in their initial
+states. It ends in a different structured state, because in $ot_2$
+both pLTS conduct transitions, showing that the control has gone from
+processes $P$ to $(acc(x);Q$, consuming actions $\delta(x)$ and
+$acc(x)$. Controller $C_1$ has only one state, but its state variable
+$s_0$ has changed to 1.
+
 \paragraph{Structural Semantic Rules:}
-Now we build the semantics of an open pNet as an open automaton where LTSs are the pLTSs at
-the leaves of the pNet structure, and the states are given by 
-Definition~\ref{def-states}. The open transitions first
+Now we build the semantics of an open pNet as an open automaton where
+LTSs are the pLTSs at 
+the leaves of the pNet structure, and the states are structured as in
+the previous section. 
+%given by Definition~\ref{def-states}.
+The open transitions first
  project the global state into states of the leaves, then apply
@@
 
-\begin{example} \emph{Using the operational rules to compute
-    open-transitions}
-  In Fig. \ref{usingrules:ot2} we show the deduction tree used to construct and prove the 
-  open transition $ot_{2}$ of \texttt{LOTOS}.
-%(see example page \pageref{OT:ccs-composed}).
-%  \TODO{Eric: change for a deduction tree of CCS expression}
-%  The proof tree uses TR1 twice, for the $l$ transition of $C_1$ and for the
-%  $b$ transition of $C_2$, then uses an action $b_P$ of hole $P$, and
-%  combines the results using the second vector of the PN2 sub-pNet, and
-%  the third vector of the top node. This yields a final $\tau$
-%  transition. The deduction tree in the figure shows how the
-%  predicates are generated in this process.
-
+\begin{example} \emph{Using the operational rules to compute  open-transitions: }
+  in Fig. \ref{usingrules:ot2} we show the deduction tree used to construct and prove the 
+  open transition $ot_2$.
 \end{example}
@@
 \end{mathpar}
-  \caption{Proof of  $ot_{2}$ (with interaction of processes $P$ and action $acc(x)$) for ``P>>(acc(x);Q)''}
+  \caption{Proof of  $ot_{2}$ (interaction of process $P$ and action $acc(x)$) for ``P>>(acc(x);Q)''}
   \label{usingrules:ot2}
@@
 
-\QIN{
-The proof tree uses TR1 twice, for the $\delta$ transition of $C_1$ and for the $acc(x)$ transition of $C_2$, then uses an action $b_{12}$ of hole $P$, and combines the results using the first vector of the PN2 sub-pNet, and the second vector of the top node according to TR2.
-This yields a final $\underline{\delta(x)}$ transition.
-The deduction tree in the figure shows how the predicates are generated in this process.
-}
-
-%% Note that while the scenario above is expressed as a single
-%% instantiation of the possible behaviours, the constructions below are
-%% kept symbolic, and each open-transition deduced expresses a whole family of
-%% behaviours, for any possible values of the variables.
-
-\paragraph{Variable management.}
+The proof tree uses TR1 twice, for the $\delta$ transition of $C_1$
+and for the $acc(x)$ transition of $C_2$, then uses an action
+$hb_{12}$ of hole $P$, and combines the results using the first vector
+of the PN2 sub-pNet, and the second vector of the top node according
+to TR2. This yields a final $\underline{\delta(x)}$ transition. The
+deduction tree in the figure shows how the predicates are generated in
+this process.
+
+\paragraph{Fresh variables management.}
 The variables in each synchronization vector are considered local:
@@
 application of Tr2 have to be fresh and all distinct. 
-This will be implemented within the open-automaton generation algorithm,
-e.g. using name generation using a global counter as a suffix.
+% This will be implemented within the open-automaton generation algorithm,
+% e.g. using name generation using a global counter as a suffix.
 
@@
 pretty-printing, but also for translating the presentation, and the
-predicates, into Z3 syntax.
+predicates, into Z3 syntax (we shall detail this translation in
+section \ref{section:pruning}).
 
@@
 	\item Sorts: Constants sets of the algebra or types of the data
-          and actions. 
+          and actions. In every presentation, sorts for integer and
+          boolean are implicitly declared.
+
 	\item Operators: Operators used to construct action
@@
 \paragraph{Sorts}
-\QIN{
-Sorts are represented by a given name, showing the ownership of the variables and constants. The
-sort of actions is built by the constant actions. There \emph{must} be one sort for actions, and eventually
-several others for the types of data parameters. In the LOTOS example, we have the $Action$ sort:
-}
+are represented by a given name, showing the ownership of the
+variables and constants. The sort of actions is built by the constant
+actions. There \emph{must} be one sort for actions, and eventually 
+several others for the types of data parameters. In the LOTOS example,
+we have the $Action$ sort:
+
 \[\OTvar{Action = } \{ l, \delta, r, p, q, acc \} .\]
 
-In every presentation, sorts for integer and boolean are implicitly declared.
-
-\paragraph{Operators}
+\paragraph{Operators:}
 %We need introduce operators for building expressions, of both action
@@
 %\rightarrow Sort_j , i_1 , ... , i_n, j \in [0..k] $.
-\QIN{
-We need introduce operators for building expressions, either action expressions or predicate terms, when encoding the algebra into pNets.
-The operators here are treated as functions, with the sorts of the pNet acting as the types of their input and output.
-}
-
-\QIN{For instance, in our LOTOS running example, we use a function ``$VOID$'' action to construct the action expression $\delta(x)$ and $acc(x)$.
+We  introduce operators for building expressions, either action
+expressions or predicate terms, when encoding the algebra into
+pNets. The operators here are treated as functions, with the sorts of
+the pNet acting as the types of their input and output. 
+For instance, in our LOTOS running example, we use a function ``$VOID$'' action to construct the action expression $\delta(x)$ and $acc(x)$.
 We can define the operator as a binary operator with the format like:
-}
 
  \[\OTvar{VOID:}\OTvar{< Action, Int >} \rightarrow \OTvar{Action .} \]
-
-\QIN{The translation of the presentation in the Z3 SMT solver will be given later.
-}
 
@@
 In this section we present an algorithm to construct the open
-automaton representing the behavior of an open pNet, and we prove that
-under reasonable conditions this automaton is finite.
+automaton representing the behavior of an open pNet, and show
+under which conditions this automaton is finite.
 
@@
 
-2b) For each of the obtained deduction trees, extract the resulting
+2b) For each deduction trees, extract the resulting
 open-transition.
-The predicate is submitted to Z3 for checking satisfiability. If it is
-NOT satisfiable, the resulting OT is discarded. This will minimize the
-number of 
-resulting transitions.
+Its predicate is checked (using Z3) for  satisfiability. If it is
+unsatisfiable, the resulting OT is discarded. This will minimize the
+number of resulting transitions.
 
@@
 
-\QIN{
-The variables in each synchronization vector are considered local, so
-does the variables of an open transition, such as its hole behaviors
-and its result action. We want all the variables unique on every occurrence of them. 
-%Similarly, the name given to the hole behaviors for each hole or the result action for each open transition must be distinct. 
-At the same time, we also hope them still
+Application of the semantic rules require generating a lot of fresh
+names, for different kind of variables. We could use a global name
+generator to garantee unicity, but 
+at the same time, we also hope them still
 readable. Here we rename the variables with a regular format using the fresh function.
-}
-\TODO{Could try to reduce the text, but give a couple examples ?[DONE]}
-
 More precisely, the fresh function generates a new name adding a
@@
 \begin{itemize}
-   \item[$\bullet$] $prefix$ is a default internal name for the variable. So far the internal name can be  sva (SV action), ra (result action), hb (hole behavior).
+   \item[$\bullet$] $prefix$ identifies the kind of the
+     variable. current kinds are: sva (SV action), ra (result action), hb (hole behavior).
    \item[$\bullet$] $tree\ index$ is the index of the node containing the variable in the tree-like structure of the pNet.
@@
 
-\QIN{
 For example, in the running example, the first possible behavior of the hole, it doesn't have a name, only have the prefix ``hb''.
@@
 The fresh variable name is ``$:hb:12:1$''.
-}
 
@@
 \subsection{Pruning the unsatisfiable results}
-
+\label{section:pruning}
 %We have used a brute-force method to generate all the possible open

### 2017-04-21 2017-Xudong-SMT/submit-ICTAC2017.tex
Improve the "related work"
The reference are unchanged. 
Change the description.

@@
 \TODO{Should be improved}
-
+\QIN{
 There is not much researches trying to develop symbolic bisimulation approaches
@@
 interacting with automatic theorem provers. The closest work is the
-one already mentionned from J. Rathke~\cite{HennessyRathke:TCS98},
+one already mentioned from J. Rathke~\cite{HennessyRathke:TCS98},
 who developed the symbolic bisimulation for a
@@
 classic works.
-
-There are other dedicated platforms, e.g. for the analyses of 
-programming languages, making use of external automatic theorem
+}
+
+\QIN{
+For other applications, e.g. for the analyses of 
+programming languages, there exist dedicated platforms making use of external automatic theorem
 provers (ATP), or even some automatic tactics from interactive theorem
-provers (ITP), to perform symbolic reasonning, and for example to
+provers (ITP), to perform symbolic reasoning, and for example to
 discharge some subgoals in the proofs.
+Tools like Rodin~\cite{deharbe2013,deharbe2014,abrial2007} have already integrated several provers, like Z3, as modules for proving the proof obligations generated from the model inputed by user.
+The prover we used, also is Z3, is developed by Microsoft Research based on the satisfiability modulo
+theories (SMT), mainly applied in extended static checking, test case
+generation, and predicate abstraction.
 In a similar way, there are several ATPs/ITPs we could consider to use for
@@
 alternative to Z3, such as CVC4~\cite{barrett:CAV2011}, Coq~\cite{armand:CPP2011,besson:CPP2011},
-Isabelle~\cite{blanchette:FroCoS2011} or others. Z3 is
-developed by Microsoft Research based on the satisfiability modulo
-theories (SMT), mainly applied in extended static checking, test case
-generation, and predicate abstraction. Tools like Isabelle and
-Rodin~\cite{deharbe2013,deharbe2014,abrial2007} have already integrated SMT solvers as modules for proving the
-theorem or formula inputed by users.
+Isabelle~\cite{blanchette:FroCoS2011} or others. 
+}
 

### 2017-04-21 2017-Xudong-SMT/submit-ICTAC2017.tex
19 pages !!!

@@
 the result pruning and bisimulation checking in our algorithm, as an
-alternative to Z3, such as CVC4~\cite{barrett:CAV2011}, Coq~\cite{armand:CPP2011,besson:CPP2011},
+alternative to Z3, such as CVC4~\cite{barrett:CAV2011},
+Coq~\cite{armand:CPP2011},
+%Coq~\cite{armand:CPP2011,besson:CPP2011},
 Isabelle~\cite{blanchette:FroCoS2011} or others. 
@@
 set of actions of a hole or a pNet), $Leaves$ and $Holes$ (all pLTSs
-(resp holes) in a pNet hierarchical system). These can be found in \cite{henrio:Forte2016}.
+(resp holes) in a pNet hierarchical system. These can be found in \cite{henrio:Forte2016}.
 %The preceding definition relies on the auxiliary functions below:
@@
 
-Theh transition in the conclusion of this rule starts in
+The transition in the conclusion of this rule starts in
 state $\ostate{00}$, where both $C_1$ and $C_2$ are in their initial
@@
 \begin{figure}[h]
+  \vspace{-10mm}
+
 \begin{mathpar}
@@
           and actions. In every presentation, sorts for integer and
-          boolean are implicitly declared.
+          boolean are implicitly declared.  There \emph{must} be one sort for actions, and eventually 
+several others for the types of data parameters. In the LOTOS example,
+we have the $Action$ sort: $\OTvar{Action = } \{ l, \delta, r, p, q, acc \} .$
 
@@
           constructors of data and action sorts, but also predicates
-          over these objects.
+          over these objects. For instance, in our LOTOS example, we
+          could have two constructor functions ``$DELTA$'' and ``$ACC$''
+          to construct the action expression $\delta(x)$ and $acc(x)$, declared as:
+          $\OTvar{DELTA:}\OTvar{< Data >} \rightarrow \OTvar{Action .}$
         \item Constants: The satisfiability solver need to know which
@@
 
-\paragraph{Sorts}
-are represented by a given name, showing the ownership of the
-variables and constants. The sort of actions is built by the constant
-actions. There \emph{must} be one sort for actions, and eventually 
-several others for the types of data parameters. In the LOTOS example,
-we have the $Action$ sort:
-
-\[\OTvar{Action = } \{ l, \delta, r, p, q, acc \} .\]
-
-\paragraph{Operators:}
 %We need introduce operators for building expressions, of both action
@@
 %\rightarrow Sort_j , i_1 , ... , i_n, j \in [0..k] $.
-We  introduce operators for building expressions, either action
-expressions or predicate terms, when encoding the algebra into
-pNets. The operators here are treated as functions, with the sorts of
-the pNet acting as the types of their input and output. 
-For instance, in our LOTOS running example, we use a function ``$VOID$'' action to construct the action expression $\delta(x)$ and $acc(x)$.
+%% We  introduce operators for building expressions, either action
+%% expressions or predicate terms, when encoding the algebra into
+%% pNets. The operators here are treated as functions, with the sorts of
+%% the pNet acting as the types of their input and output. 
+%% For instance, in our LOTOS running example, we use a function ``$ACT$'' action to construct the action expression $\delta(x)$ and $acc(x)$.
 We can define the operator as a binary operator with the format like:
 
- \[\OTvar{VOID:}\OTvar{< Action, Int >} \rightarrow \OTvar{Action .} \]
+%%  \[\OTvar{ACT:}\OTvar{< Action, Int >} \rightarrow \OTvar{Action .} \]
 
@@
 later). From these, we compute
-the open automaton of an open pNet by directly
-implementing the sketch showed before. However, we made some
-modifications due to implementation choices.
+the open automaton of an open pNet. We explain here our main
+implementation choices.
 %:
@@
 The format of \emph{fresh variable} (renaming) is defined as:
-$$\emph{prefix : tree\ index\ :\ counter}$$
+``$\emph{prefix : tree\ index\ :\ counter}$''.
 \begin{itemize}
@@
 
-For example, in the running example, the first possible behavior of the hole, it doesn't have a name, only have the prefix ``hb''.
-The hole is the second subnets of the root node so its ``tree index'' is ``12''.
-The fresh variable name is ``$:hb:12:1$''.
-
-\TODO{I have not yet been in details through the next section, but we
-  need to shorten them...}
+For example, in the running example, the first possible behavior of
+the hole, it doesn't have a name, only have the prefix ``hb''. The
+hole is the second subnets of the root node so its ``tree index'' is
+``12''. The fresh variable name is ``$\OTvar{:hb:12:1}$''.
+
+%\TODO{I have not yet been in details through the next section, but we
+%  need to shorten them...}
 
@@
 
-\QIN{
-Every time applying Tr2, we conduct combining and matching to generate predicates.
-The predicate of the open transition is a conjunction of two parts. The first part, which is the simpler one, composes the predicate from the
+Our implementation does not build explicitely the proof trees for each
+open transition, but instead : [Combining] enumerate all possible combinations of
+pLTS transition (using TR1) and each synchronisation vector choice
+(TR2); [Matching] build the corresponding transition, and in particular
+its predicate, in a hierarchical manner.
+Each time we apply Tr2, we build a predicate as a conjunction of two
+parts. The first part, which is the simpler one, composes the
+predicate from the 
 subnets and the guard from transitions in sub-pLTS or synchronization
@@
 vectors.
-}
+
 %Note that it is simple to collect required terms in the first
@@
 % 6. Return the result list.
-\paragraph{Combining}
+
 %We first conduct combining. For each subnet, we enumerate all the
@@
 We get much more combinations after combining $ot$ from $L_{ot}$ with the partial result.
-\QIN{
-Algorithm 1 shows the combining algorithm for enumerating all the possible the possible working status combinations of subnets.
-Dealing with the list $TR$ containing several sets of open transitions from different subnets, the algorithm  chooses one of sets $L_{ot}$ and does combining on the remaining part of $TR$ recursively.
-Since there could exist the case that the subnet is not working, a $null$ is added into the $L_{ot}$ to represent it.
-We get much more combinations after combining $ot$ with the partial result.
-}
+
+\paragraph{Combining:}
+Algorithm 1 shows the combining algorithm for enumerating all possible
+working status combinations from subnets. Dealing with a list $TR$
+containing  sets of open transitions from different subnets,
+the algorithm choses one of sets $L_{ot}$ and does combining on the
+remaining part of $TR$ recursively. The case when a subnet is not working is
+managed by adding a $null$ into the $L_{ot}$.
 
@@
 % 5. Return the result list of all the possible OTs.
-\paragraph{Matching}
 
@@
 			\State Skip;
-			\Else 
-			\State Add $(e_1 = e_2)$ into the $Pred$;
+			\Else ~ Add $(e_1 = e_2)$ into the $Pred$;
 			\EndIf
@@
 \end{algorithm}
-\QIN{
-Algorithm 2 shows the algorithm matches combination $L_C$, hole behaviors $B$ with synchronization vectors $SV$ according to the definition of the predicate declared before.
+
+\paragraph{Matching:} Algorithm 2 shows the algorithm matches combination $L_C$, hole behaviors $B$ with synchronization vectors $SV$ according to the definition of the predicate declared before.
 We clone the $sv$ using the fresh function to generate a new $sv'$ with fresh variables.The mismatch on working status is easy to detect so we filter them in the algorithm through checking the matching elements $e_1$ and $e_2$.
-}
 
@@
 
-\subsection{Management of assignments}
+\subsection{Management of state variable assignements}
 %The pLTS contains some variables in each of its states (state
@@
 %our algorithm.
-\QIN{
-There are some assignment on the variables in each of states of the pLTS (state variables), or just as global states of it (global variables).
+
+In a pLTS, there may be several incoming transitions of some states
+that assign potentialy different values to a state variable.
+To handle such cases, the algorithm manages the variables together
+with a list for each pLTS.
+The list we used contains several triples <$v$, $S$, $AssignRH$> 
+where $v$ is the variable in pLTS, $S$ is its owner state and
+$AssignRH$ is a list of expressions over other variables in the right
+hand side of assignments of $v$.
+As a pragmatic extension to the formal definition, we also manage
+``global variables'' that are defined in all states of the pLTS.
+
+%There are some assignment on the variables in each of states of the pLTS (state variables), or just as global states of it (global variables).
 There is usually not only one assignment for a state variable, miss of them may drop the unsatisfiable results.
-In order to avoid such mistakes, the algorithm manages the variables together with a list for each pLTS.
-}
-
-\QIN{
-The list we used contains several triples <$v$, $S$, $AssignRH$> to record the information of both state and global variables of the pLTS, where $v$ is the variable in pLTS, $S$ is its owner state and $AssignRH$ is a list of expressions over other variables in the right hand side of assignments of $v$.
-It means the variable is global in the pLTS belonging to all the states, if $S$ is $null$.
-We update the list of record triples every time Tr1 is applied.
-Then we can track all the possible value of the variables when computing open transitions.
-}
+In order to avoid such mistakes,
+
+%% \QIN{
+%% The list we used contains several triples <$v$, $S$, $AssignRH$> to
+%% record the information of both state and global variables of the pLTS,
+%% where $v$ is the variable in pLTS, $S$ is its owner state and
+%% $AssignRH$ is a list of expressions over other variables in the right
+%% hand side of assignments of $v$. It means the variable is global in
+%% the pLTS belonging to all the states, if $S$ is $null$. We update the
+%% list of record triples every time Tr1 is applied. Then we can track
+%% all the possible (symbolic) value of the variables when computing open transitions.
+%% }
 
@@
 \QIN{
-So when we declare the operator VOID we illustrated in section 4.1, it will be just declared together with the constants likes:
-}
-
-\[\OTvar{(VOID\ (action3\ Action)(data\ Int)) .}\]
+So when we declare the operator ACT we illustrated in section 4.1, it will be just declared together with the constants likes:
+}
+
+\[\OTvar{(ACT\ (action3\ Action)(data\ Int)) .}\]
 
@@
 
-\[\OTvar{(declare\text{-}fun\ VOID\ (Action\ Int)\ Action) .}\]
+\[\OTvar{(declare\text{-}fun\ ACT\ (Action\ Int)\ Action) .}\]
 %Although in Fig~\ref{schema:smt-lib} we have not declared $functions$ outside of $datatypes$, there still exists $functions$ declared independently.

### 2017-04-21 2017-Xudong-SMT/submit-ICTAC2017.tex
nerly done !!!

@@
 \TODO{Should be improved}
-\QIN{
+
 There is not much researches trying to develop symbolic bisimulation approaches
@@
 classic works.
-}
 
@@
 
-\paragraph{Matching:} Algorithm 2 shows the algorithm matches combination $L_C$, hole behaviors $B$ with synchronization vectors $SV$ according to the definition of the predicate declared before.
-We clone the $sv$ using the fresh function to generate a new $sv'$ with fresh variables.The mismatch on working status is easy to detect so we filter them in the algorithm through checking the matching elements $e_1$ and $e_2$.
-
+\paragraph{Matching:} Algorithm 2 shows the algorithm matches
+combination $L_C$, hole behaviors $B$ with synchronization vectors
+$SV$ according to the definition of the predicate declared before. We
+clone the $sv$ using the fresh function to generate a new $sv'$ with
+fresh variables.The mismatch on working status is easy to detect so we
+filter them in the algorithm through checking the matching elements
+$e_1$ and $e_2$. 
 Then we build the resulting open transition. Satisfiability of the
@@
 As a pragmatic extension to the formal definition, we also manage
-``global variables'' that are defined in all states of the pLTS.
+``global variables'', defined in all states of the pLTS.
 
@@
 transitions in the open automaton, using all possible combinations of
-synchronisation vectors. Naturally this builds open transtions where
+synchronisation vectors. Naturally this builds some transtions where
 the predicates express uncompatible constraints. Even if having an
-unsatisfiable transition in the open automaton would not be incorrect,
+unsatisfiable (symbolic) transition in the open automaton would not be incorrect,
 we want to check them for satisfiability, and reduce the number of
@@
 the controller C1 wants to move the control from $P$ to $(acc(x);Q)$,
-conducting a $\delta$ transition. However, the first synchronization
-vector is chosen, we can easily find the contradiction in the
-generated predicate term ``$:ra:11:1=l \!\land\! \delta=:ra:11:1$''.
+conducting a $\delta$ transition. However, a synchronization
+vector is chosen that does not match with this behavior, and we can
+easily find the contradiction in the 
+generated predicate term ``$\OTvar{:ra:11:1}=l \!\land\! \delta=\OTvar{:ra:11:1}$''.
 
 Checking satisfiability requires some symbolic computation
-on the action expressions and the predicates, and this reasoning
+on the action expressions and the predicates, and this 
 may depend on the specific theory of the action algebra. 
-We choose to use the SMT solver Z3 as the checker for the open
-transitions considering the predicates may contain the expression
+We choose to use the SMT solver Z3 as the checker engine, considering
+the predicates may contain the expression 
 using uninterpreted functions declared by users.
 The ``Modulo Theory'' part of SMT solvers is important here, so that
-the solver can use specific properties of the action algebra.
+the solver can use specific properties of each action algebra.
 
@@
 
-\begin{figure}[t]
-  \centerline{\includegraphics[width=10cm]{XFIG/Interaction}}
-  \caption{The architecture of the interaction between pNet API and Z3}  \label{schema:interaction}
-\end{figure}
+%% \begin{figure}[t]
+%%   \centerline{\includegraphics[width=10cm]{XFIG/Interaction}}
+%%   \caption{The architecture of the interaction between pNet API and Z3}  \label{schema:interaction}
+%% \end{figure}
 
@@
 predicate to be checked, encoded as a set of assertions.
-
-\QIN{
-Generally, some $datatypes$ are declared to input the sorts, while here we only declare one $datatypes$ named $Action$ to involve all the constant actions.
-The $Int$ and $Bool$ are already existed in Z3.
-Then we input the predicate of that open transition in two parts.
-The variables contained in the predicate are declared first, then the terms of predicate are inputed as $assertions$ one by one.
-The result "unsat" in the output is just what we expected.
-}
+Generaly, some $datatypes$ are declared to input the sorts, while here
+we only declare one $datatypes$ named $Action$ to involve all the
+constant actions. Then we input the predicate of that open transition
+in two parts. The variables contained in the predicate are declared
+first, then the terms of predicate are inputed as $assertions$ one by
+one. The result "unsat" in the output is just what we expected.
 
@@
 %translated into $datatypes$ and $functions$ then submitted to the Z3
-%at the same time.
-Each candidate predicate will then be translated into $assertions$ before submitted to Z3 after the algorithm computing out all the possible open transitions, they act as intermediate results there.
-Together with the $datatypes$ and $functions$, the $assertions$ are used to check the satisfiability of the predicate in Z3.
-\QIN{
-We present the architecture of the interaction with Z3 in
-Fig~\ref{schema:interaction}. For each OT generated at the top level
-of a pNet, the predicate must be submitted for satisfiability check to
-Z3.
-For that we need to translate the algebra $presentation$, the predicates and the variable assignments (the Post part) into Z3 (Java-API) syntax.
-The $presentation$ and the predicates are translated separately.
-}
+%at the same time. Each candidate predicate will then be translated
+%into $assertions$ before submitted to Z3 after the algorithm
+%computing out all the possible open transitions, they act as
+%intermediate results there. Together with the $datatypes$ and
+%$functions$, the $assertions$ are used to check the satisfiability of
+%the predicate in Z3.
+
+To build the input submitted to Z3 for each OT,
+we translate the algebra $presentation$, the predicates and the
+variable assignments (the Post part) into Z3 (Java-API) syntax.
+% The $presentation$ and the predicates are translated separately.
 
@@
 
-The $datatypes$ are declared according to the $sorts$ the users declared in the $presentation$.
-If the return type of the $functions$ is one of the $datatypes$, we add this $function$ when declare the $datatypes$, it present the reality that every action expression also belongs to a sort of pNet.
-
-\QIN{
-So when we declare the operator ACT we illustrated in section 4.1, it will be just declared together with the constants likes:
-}
-
-\[\OTvar{(ACT\ (action3\ Action)(data\ Int)) .}\]
-
-\QIN{
-The $functions$ can also be declared independently, it usually applies to functions return integer or boolean, in the format likes:
-}
-
-\[\OTvar{(declare\text{-}fun\ ACT\ (Action\ Int)\ Action) .}\]
+The $datatypes$ are declared according to the $sorts$ the users
+declared in the $presentation$. If the return type of the $functions$
+is one of the $datatypes$, we add this $function$ to the $datatypes$ declaration.
+So when we declare the operator ACT we illustrated in section 4.1, it
+will be just declared together with the constants like :\\
+\centerline{$\OTvar{(ACT\ (action3\ Action)(data\ Int))}$}
+
+The $functions$ can also be declared independently, it usually applies to functions returning integer or boolean, in the format like:\\
+\centerline{$\OTvar{(declare\text{-}fun\ ACT\ (Action\ Int)\ Action)}$}
+
 %Although in Fig~\ref{schema:smt-lib} we have not declared $functions$ outside of $datatypes$, there still exists $functions$ declared independently.
@@
 %After that, for the assignments of the different variables, we generate a conjunction of them. This way we obtain a new term of the predicate involving assignments of the variables.
-\QIN{
-The assignments are also treated as a term of predicates when checking the satisfiability.
-Here we need conduct some translations, such as $\{s_0 \leftarrow 1\}$ in \ref{section:op-semantics}, we translate it into an equation $s_0=1$.
-Then for the assignments of the same variable, we do not figure out which state is the precursor of current state, we keep all these possible equations instead, and generate the disjunction of these equations.
-Correspondingly, we generate a conjunction for the assignments from the different variables.
-In this way, we obtain a new term of the predicate.
-}
+
+State-variable assignments are also treated as a part of the
+predicates when checking the satisfiability. Here we need conduct some
+translations, such as $\{s_0 \leftarrow 1\}$ in
+\ref{section:op-semantics}, we translate it into an equation
+$s_0=1$. Then for the assignments of the same variable, we keep all
+possible equations, and generate the disjunction of
+these equations. Correspondingly, we generate a conjunction for the
+assignments from the different variables.
 
@@
 % transitions, we check them one by one.
-Here we declare the variables in the predicate first to make Z3 know all the parameters used for checking this time.
-The variable including the argument in the operators must has its sort as every pNet defines two default sorts $Int$, $Bool$ default and at least one sort for the actions.
-The variables can declared using the $datatypes$ declared in the format as:
-
-\[\OTvar{(declare-const\ |:ra:1:1|\ Action) .}\]
-
-The predicate submitted to the Z3 contain the assignments as them
-become a part of predicate after our translation. Each term of the
+Here we declare first all the variables in the predicates, with their
+sorts.
+An example of syntax is::\\
+\centerline{$\OTvar{(declare-const\ |:ra:1:1|\ Action)}$}
+
+\noindent Then each term of the
 predicate is an assertion in Z3, as an example, in the former
-unsatisfiable result in Fig~\ref{schema:unsat-ot}, the contradiction is occured in terms:
-
-\[\OTvar{(:ra:11:1=l)} \OTland \OTvar{(delta=:ra:11:1) .}\]
-
-from which we generate the following two assertions:
-
-\[\OTvar{(assert\ (=\ |:ra:11:1|\ l))\ \ \ (assert\ (=\ delta\ |:ra:11:1|)) .}\]
+unsatisfiable result in Fig~\ref{schema:unsat-ot}, the contradiction is occured in terms: \\
+\centerline{$\OTvar{(:ra:11:1=l)} \OTland \OTvar{(delta=:ra:11:1)}$}\\
+from which we generate the following two assertions:\\
+\centerline{$\OTvar{(assert\ (=\ |:ra:11:1|\ l))\ \ \ (assert\ (=\ delta\ |:ra:11:1|))}$}
+
+\noindent The predicate submitted to the Z3 also contains the
+assignments encodings.
+In the case of $ot_2$, it
+gives the assertion:\\
+\centerline{$\OTvar{assert (or (= var\_s0 0) (= var\_s0 01)))}$}
 
@@
 
-\QIN{
-We get the final result after pruning all the unsatisfiable open transitions and only 5 results left; the resulting open automaton is shown in Fig.
-~\ref{schema:lotos-result}, we have drawn manually the open automaton obtained as the final result generated by algorithm.
-}
+Running our algorithm for our LOTOS example yields 30 open
+transitions, out of which 25 are detected unsatisfiable by Z3, so we
+get only 5 results left; the resulting open automaton is shown in
+Fig. ~\ref{schema:lotos-result}, we have drawn manually the open
+automaton obtained as the final result generated by algorithm.
 

### 2017-04-21 2017-Xudong-SMT/submit-ICTAC2017.tex
Modify the section 5.2.
Adjust the position of two algorithm.

@@
 called parameterized labelled transition systems (pLTS), where each
-hierarchical level defines the possible synchronisation of the lower levels.
-Traditionaly, pNet have been used to formalize full
+hierarchical level defines the possible synchronization of the lower levels.
+Traditionally, pNet have been used to formalize full
 defined systems or softwares. But we want also to define and reason
@@
 automaton computing and needs to satisfy the constraints expressed as
-the rules of the operationnal semantics. So in
+the rules of the operational semantics. So in
 the computing algorithm, computing open transitions is necessary and
@@
   semantics rules, and add features in the algorithm to deal the full
-  model, including management of variables and assignements.}
+  model, including management of variables and assignments.}
 %  \item We extended the meta-model of action expressions, and the
@@
 mechanism, based on unification between two or more action
-expressions. This will be used in the semantics of synchronisation
+expressions. This will be used in the semantics of synchronization
 vectors to express various kinds of communication or synchronization mechanisms.
@@
 internal actions is given by  \emph{synchronization vectors}: a
-synchronization vector synchronises one or several internal actions, and
+synchronization vector synchronizes one or several internal actions, and
 exposes a single resulting global action.
@@
 the main features of pNets and the way we deal with them in the symbolic
-semantics, and in the satifiability checking.
+semantics, and in the satisfiability checking.
 
@@
 Three synchronization vectors are defining the possible
-synchronisations between the actions of the subnets.
+synchronizations between the actions of the subnets.
  The first
@@
 action $a_2$ of Q.  
-Similarily the node PN2 has two synchronization vectors to encode
+Similarly the node PN2 has two synchronization vectors to encode
 the behavior of the Prefix operator.
@@
 
-3) Finaly a reachability check could potentialy
+3) Finally a reachability check could potentially
 prune the state space.
@@
 In our prototype we start directly with open pNets expressed
-programmaticaly, using the pNet API (graphical editors may be added
+programmatically, using the pNet API (graphical editors may be added
 later). From these, we compute
@@
 names, for different kind of variables. We could use a global name
-generator to garantee unicity, but 
+generator to guarantee unicity, but 
 at the same time, we also hope them still
@@
 
-\begin{algorithm}
-\caption{Combining}
-\begin{algorithmic}[1]
-
-%\Require The list $TR$ of the open transition sets of the subnets. 
-%\Ensure The list of all the possible combinations of open transitions $L_C$.
-\State Initialise an empty combination list $L_C$;
-\State Extract a list of open transitions $L_{ot}$ from $TR$;
-\State Add $null$ to $L_{ot}$;
-\State Get the combinations $L'_C$ of the $TR$;
-\For{each $ot \in L_{ot}$}
-	\For{each $C' \in L'_C$}
-		\State Add $ot$ into $C'$ to get a new tuple $C$;
-		\State Add $C$ into $L_C$;
-	\EndFor
-\EndFor 
-\State \Return $L_C$;
-
-\end{algorithmic}  
-\end{algorithm}
-
-Our implementation does not build explicitely the proof trees for each
+Our implementation does not build explicitly the proof trees for each
 open transition, but instead : [Combining] enumerate all possible combinations of
-pLTS transition (using TR1) and each synchronisation vector choice
+pLTS transition (using TR1) and each synchronization vector choice
 (TR2); [Matching] build the corresponding transition, and in particular
@@
 
+\begin{algorithm}
+\caption{Combining}
+\begin{algorithmic}[1]
+
+%\Require The list $TR$ of the open transition sets of the subnets. 
+%\Ensure The list of all the possible combinations of open transitions $L_C$.
+\State Initialize an empty combination list $L_C$;
+\State Extract a list of open transitions $L_{ot}$ from $TR$;
+\State Add $null$ to $L_{ot}$;
+\State Get the combinations $L'_C$ of the $TR$;
+\For{each $ot \in L_{ot}$}
+	\For{each $C' \in L'_C$}
+		\State Add $ot$ into $C'$ to get a new tuple $C$;
+		\State Add $C$ into $L_C$;
+	\EndFor
+\EndFor 
+\State \Return $L_C$;
+
+\end{algorithmic}  
+\end{algorithm}
+
 % Mixing is to match the combination of the subnets' open transitions, hole behaviors and result action with the SV (synchronization vector) to generate the possible predicates of the OT (open transition).
@@
 %out.
+
+\paragraph{Matching:} Algorithm 2 shows the algorithm matches
+combination $L_C$, hole behaviors $B$ with synchronization vectors
+$SV$ according to the definition of the predicate declared before. We
+clone the $sv$ using the fresh function to generate a new $sv'$ with
+fresh variables.The mismatch on working status is easy to detect so we
+filter them in the algorithm through checking the matching elements
+$e_1$ and $e_2$. 
+Then we build the resulting open transition. Satisfiability of the
+predicate is not checked at this level, but only later, at the
+toplevel of the pNet.
 
@@
 
-\paragraph{Matching:} Algorithm 2 shows the algorithm matches
-combination $L_C$, hole behaviors $B$ with synchronization vectors
-$SV$ according to the definition of the predicate declared before. We
-clone the $sv$ using the fresh function to generate a new $sv'$ with
-fresh variables.The mismatch on working status is easy to detect so we
-filter them in the algorithm through checking the matching elements
-$e_1$ and $e_2$. 
-Then we build the resulting open transition. Satisfiability of the
-predicate is not checked at this level, but only later, at the
-toplevel of the pNet.
-
-\subsection{Management of state variable assignements}
+\subsection{Management of state variable assignments}
 %The pLTS contains some variables in each of its states (state
@@
 In a pLTS, there may be several incoming transitions of some states
-that assign potentialy different values to a state variable.
+that assign potentially different values to a state variable.
 To handle such cases, the algorithm manages the variables together
@@
 transitions in the open automaton, using all possible combinations of
-synchronisation vectors. Naturally this builds some transtions where
-the predicates express uncompatible constraints. Even if having an
+synchronization vectors. Naturally this builds some transitions where
+the predicates express incompatible constraints. Even if having an
 unsatisfiable (symbolic) transition in the open automaton would not be incorrect,
@@
 The input to Z3 contains the declaration of the LOTOS action algebra types
-and constructors, then the declaration of variables, and finaly the
+and constructors, then the declaration of variables, and finally the
 predicate to be checked, encoded as a set of assertions.
-Generaly, some $datatypes$ are declared to input the sorts, while here
+Generally, some $datatypes$ are declared to input the sorts, while here
 we only declare one $datatypes$ named $Action$ to involve all the
@@
 predicates when checking the satisfiability. Here we need conduct some
-translations, such as $\{s_0 \leftarrow 1\}$ in
-\ref{section:op-semantics}, we translate it into an equation
+translations, such as $\{s_0 \leftarrow 1\}$ in section
+~\ref{section:op-semantics}, we translate it into an equation
 $s_0=1$. Then for the assignments of the same variable, we keep all
@@
 predicate is an assertion in Z3, as an example, in the former
-unsatisfiable result in Fig~\ref{schema:unsat-ot}, the contradiction is occured in terms: \\
+unsatisfiable result in Fig~\ref{schema:unsat-ot}, the contradiction is occurred in terms: \\
 \centerline{$\OTvar{(:ra:11:1=l)} \OTland \OTvar{(delta=:ra:11:1)}$}\\
@@
 contain predicates which do not represent any possible concrete
-instanciations. 
-To get rid of these useless transtions, we use a SMT solver Z3 for checking the
+instantiations. 
+To get rid of these useless transitions, we use a SMT solver Z3 for checking the
 satisfiability of the predicate in each open transition. In

### 2017-04-21 2017-Xudong-SMT/submit-ICTAC2017.tex
finished ??

@@
 \newcommand{\OTvar}{\texttt}
-\newcommand{\OTland}{\ \land\ }
+\newcommand{\OTland}{\;\land\ }
 \definecolor{airforceblue}{rgb}{0.26, 0.44, 0.56}
@@
   between INRIA and ECNU, Shanghai}}
-\author{ Xudong Qin\inst{3}  \ \ \  Eric Madelaine\inst{1,2}} 
+\author{ Xudong Qin\inst{2,3}  \ \ \  Eric Madelaine\inst{1,2}
+  \ \ \  Min Zhang\inst{3}} 
 \institute{Univ. of Nice Sophia Antipolis, CNRS, UMR 7271, 06900 Sophia Antipolis, France
@@
 \begin{abstract}
-  \TODO{not good for a conference, (to be rewriten by Eric)}
-  We implement the symbolic semantics of open pNets using their
-  so-called ``Open Automaton'' behavioral semantics. This involve
-  building predicates expressing the synchronization conditions
-  allowing some combination of events in the pNet system. These
-  predicates are typically built using first order logic, plus some
-  predicates specific of particular action algebras. To reduce the
-  complexity of the generated open automata, we use the Z3 SMT engine
-  to check satisfiability of the predicates, and prune the state
-  space..
+  %% \TODO{not good for a conference, (to be rewriten by Eric)}
+  %% We implement the symbolic semantics of open pNets using their
+  %% so-called ``Open Automaton'' behavioral semantics. This involve
+  %% building predicates expressing the synchronization conditions
+  %% allowing some combination of events in the pNet system. These
+  %% predicates are typically built using first order logic, plus some
+  %% predicates specific of particular action algebras. To reduce the
+  %% complexity of the generated open automata, we use the Z3 SMT engine
+  %% to check satisfiability of the predicates, and prune the state
+  %% space..
+
+  Open pNets are used to model the behavior of open
+  synchronous or asynchronous systems expressed in various calculi
+  or languages. They are endowed with a symbolic operational semantics
+  in terms of so-called ``Open Automata''. We implement an algorithm
+  computing this semantics, and building predicates expressing the
+  synchronization conditions allowing some combination of events in
+  the pNet system. Checking such predicates requires symbolic
+  reasoning over first order logics, and specific functions of each
+  action algebra. To reduce the complexity of the generated open
+  automata, we use the Z3 SMT engine to check satisfiability of the
+  predicates, and minimize the number of significant symbolic
+  transitions.
 
@@
 pNets provides the core low-level semantic formalism for VerCors, and
-is made of a hierarchical composition of (value-passing) automatas,
+is made of a hierarchical composition of (value-passing) automata,
 called parameterized labelled transition systems (pLTS), where each
 hierarchical level defines the possible synchronization of the lower levels.
-Traditionally, pNet have been used to formalize full
+Traditionally, pNets have been used to formalize fully
 defined systems or softwares. But we want also to define and reason
@@
 property.  
-
 The pNet model was developed in a series of
-works~\cite{HMZ:PDP15,henrio:Forte2016} and some examples have been
-introduced showing its ability in encoding the operators from some
-other algebras or  program skeletons. It is just the first step of
-our long-term goals. The operational semantic of the open pNet has
+papers~\cite{HMZ:PDP15,henrio:Forte2016} and some examples have been
+introduced showing its ability to encode the operators from some
+other algebras or  program skeletons. The operational semantic of the open pNet has
 already been defined, but we only had a sketch about how to compute it and
@@
 Computing the open transitions from the composition of pNet is the
-main part of the open 
-automaton computing and needs to satisfy the constraints expressed as
-the rules of the operational semantics. So in
-the computing algorithm, computing open transitions is necessary and
-should have some method to keep them satisfying the constraints.
+main part of the algorithm and needs to satisfy the constraints expressed as
+the rules of the operational semantics.
 Computing open automata by hand is complicated and error prone. And
@@
 \begin{itemize}
-\item \ERIC{We have refined the open automaton generation algorithm, to make
+\item We have refined the open automaton generation algorithm, to make
   it implementable, and we implemented a full working prototype, within the
@@
   semantics rules, and add features in the algorithm to deal the full
-  model, including management of variables and assignments.}
+  model, including management of variables and assignments.
 %  \item We extended the meta-model of action expressions, and the
@@
     generated by the algorithm.
-    \item \ERIC{We validated the whole approach on a small use-case covering all
-      important features of the model.}
+    \item We validated the whole approach on a small use-case covering all
+      important features of the model.
 \end{itemize}
@@
 %%   B-tools, or others like CVC4, as possible alternative to Z3}
-
-\TODO{Should be improved}
 
@@
 
-\QIN{
 For other applications, e.g. for the analyses of 
-programming languages, there exist dedicated platforms making use of external automatic theorem
+programming languages, there exist dedicated platforms making use of
+external automatic theorem 
 provers (ATP), or even some automatic tactics from interactive theorem
@@
 discharge some subgoals in the proofs.
-Tools like Rodin~\cite{deharbe2013,deharbe2014,abrial2007} have already integrated several provers, like Z3, as modules for proving the proof obligations generated from the model inputed by user.
-The prover we used, also is Z3, is developed by Microsoft Research based on the satisfiability modulo
+Tools like Rodin~\cite{deharbe2013,deharbe2014,abrial2007} have
+already integrated several provers, like Z3, as modules for proving
+the proof obligations generated from the model inputed by user. 
+The prover we used, also is Z3, is developed by Microsoft Research
+based on the satisfiability modulo 
 theories (SMT), mainly applied in extended static checking, test case
@@
 Isabelle~\cite{blanchette:FroCoS2011} or others.
-}
 
@@
 synchronization structures in distributed or parallel languages.
-In this paper, we use a running example inspired from Lotos, to illustrate
+In this paper, we use an example inspired from Lotos, to illustrate
 the main features of pNets and the way we deal with them in the symbolic
@@
 \begin{figure}[h]
-  \centerline{\includegraphics[width=8cm]{XFIG/LOTOSFormula.eps}}
+  \centerline{\includegraphics[width=10cm]{XFIG/LOTOSFormula.eps}}
   \caption{pNet encodings for the LOTOS expression}  \label{schema:lotos-pnet}
@@
 conducting a $\delta$ transition. However, a synchronization
-vector is chosen that does not match with this behavior, and we can
+vector is chosen that does not match with this action, and we can
 easily find the contradiction in the 
-generated predicate term ``$\OTvar{:ra:11:1}=l \!\land\! \delta=\OTvar{:ra:11:1}$''.
+generated predicate term ``$\OTvar{:ra:11:1}=l \!\OTland\! \delta=\OTvar{:ra:11:1}$''.
 
@@
 \begin{figure}[t]
-  \centerline{\includegraphics[width=11cm]{XFIG/SMTLIB2}}
+  %  \centerline{\includegraphics[width=12cm]{XFIG/SMTLIB2}}
+    \centerline{\includegraphics[width=\linewidth]{XFIG/SMTLIB2}}
   \caption{The input of the Z3 solver in SMT-LIB language and the output result}  \label{schema:smt-lib}
@@
 
-\QIN{The $ot_1$ shows that only the actions of the process $P$ could be transmitted out before the value $x$ being captured which is represented by the $ot_2$.
-The other 3 open transitions shows the behaviors of the process $Q$ while the $ot_3$ and $ot_4$ won't be performed as the controller has already set the value $s_0$ to 1 in the previous action.
-}
-
-\QIN{
-To sum up, from the pNet encoding LOTOS formula inputed by the user we generate the open transitions and prune the unsatisfiability automatically.
-The final result open transitions represent all the possible movements of the LOTOS example.
-They can exactly construct the open automaton for the given example.
-}
+The $ot_1$ transition means that the actions of the process $P$ could
+be transmitted out, until $P$ performs a $\delta(x)$ and the value of
+$x$ is transmitted, through transition
+$ot_2$. The other 3 open transitions shows the behaviors of the
+process $Q$ while the $ot_3$ and $ot_4$ won't be performed as the
+controller has already set the value $s_0$ to 1 in the previous
+action.
+
+To sum up, from the pNet encoding LOTOS expression, inputed by the user, we
+generate the open transitions and prune the unsatisfiability
+automatically. The final result open transitions represent all the
+possible movements of the LOTOS example. They can exactly construct
+the open automaton for the given example.
 

### 2017-06-19 2017-Xudong-SMT/submit-ICTAC2017.tex
Paper improved.
Modify the first two section and the result explanation (chapter 5.5).
Modification suggestion on section 2 and 4.

@@
 the rules of the operational semantics.
-Computing open automata by hand is complicated and error prone. And
-the algorithm published in \cite{henrio:Forte2016} was not precise
-enough for an implementation. Our first goal was then to refine the
+Computing open automata by hand is complicated and error prone.
+
+\QIN{
+And the algorithm published in \cite{henrio:Forte2016} was not the algorithm we are using
+so far, which is more precise, defining more details of the algorithm, such as the application of 
+the rules on the detection of open transitions and the management of the "data" expressions. 
+}
+
+%And
+%the algorithm published in \cite{henrio:Forte2016} was not precise
+%enough for an implementation. 
+Our first goal was then to refine the
 algorithm, and implement it in a tool.
@@
 
-There is not much researches trying to develop symbolic bisimulation approaches
+There is not much research work towards trying to develop symbolic bisimulation approaches
 for the value-passing process algebra and languages, as our long-term goals,
@@
 the proof obligations generated from the model inputed by user. 
-The prover we used, also is Z3, is developed by Microsoft Research
+The prover we used, which also happens to be Z3, is developed by Microsoft Research
 based on the satisfiability modulo 
@@
 \mathcal{E}_P\cap\mathcal{A}_P=\emptyset$;
-naturally action terms will use data expressions as subterms.
-To be able to reason about the data flow between pLTSs, we
+naturally action terms will use data expressions as sub-terms.
+
+\QIN{[We haven't used the input variables in this paper, we can remove them.]}
+\QIN{[To be able to reason about the data flow between pLTSs, we
 distinguish \emph{input variables} of the form $?x$ within terms; the function
 $\vars(t)$ identifies the set of variables in a term
-$t\in\AlgT$, and $iv(t)$ returns its input variables.
+$t\in\AlgT$, and $iv(t)$ returns its input variables.]}
 
@@
 manipulated, defined, or accessed inside states, actions, guards, and
-assignments. Without loss of generality and to simplify the formalization, we suppose 
-here that variables are local to 
-state: each state has its set of variables disjoint from the others. Transmitting 
-variable values from one state to the other can be done by explicit assignment. 
+assignments.
+
+%Without loss of generality and to simplify the formalization, we suppose 
+%here that variables are local to 
+%state: each state has its set of variables disjoint from the others. Transmitting 
+%variable values from one state to the other can be done by explicit assignment. 
+\QIN{
+Each state has its set of variables called state variables.
+$State\ variables$ can only be modified by the assignment in the transitions targeting its owner state. 
+A global state variable of a pLTS is a variable $x$ satisfying $\forall s\!\in\! S .\, x\!\in\! \vars(s)$.
+}
+
 %Similarly, to simplify the management of variables and without loss of expressivity, we 
@@
   \alpha\in\AlgA&::=&a(p_1,\ldots,p_n)&\text{action terms}\\
-  p_i&::=& ?x~|~\symb{Expr}&\text{parameters (input variable or expression)}\\
+  p_i&::=& ~\symb{Expr}&\text{parameters}\\
   \symb{Expr}&::=& \symb{Value}~|~x~|~\symb{op}(\symb{Expr}_1,..,\symb{Expr}_n)&\text{Expressions}
@@
 \]
-The input variables in an action term are those marked with a
+%\[
+%\begin{array}[l]{rcl@{\quad}p{5.5cm}}
+%  \alpha\in\AlgA&::=&a(p_1,\ldots,p_n)&\text{action terms}\\
+%  p_i&::=& ?x~|~\symb{Expr}&\text{parameters (input variable or expression)}\\
+%  \symb{Expr}&::=& \symb{Value}~|~x~|~\symb{op}(\symb{Expr}_1,..,\symb{Expr}_n)&\text{Expressions}
+%\end{array}
+%\]
+\QIN{
+[The input variables in an action term are those marked with a
 $\symb{?}$.
@@
 appear somewhere else in the same action term:
-$p_i=?x\Rightarrow\forall j\neq i.\, x\notin \vars(p_j)$
+$p_i=?x\Rightarrow\forall j\neq i.\, x\notin \vars(p_j)$]}
 
@@
 The $x_j$ here are $state\ variables$ of state $s'$.
-$State\ variables$ can only be modified by the assignment in the transitions targetting its owner state.
-A global state variable of a pLTS is a variable $x$ satisfying $\forall s\!\in\!
-S .\, x\!\in\!
-\vars(s)$.
 
@@
 variable $s_0$ encoding the change of control point from the left to
-the right sub-net.
+the right subnet.
 %% The transitions in the pLTS have the more general syntax:
@@
 It should be easy to see that this pNet system encodes properly the
-behavioral semantics of the corresponding Lotos expression. Remark
+behavioral semantics of the corresponding Lotos expression. We remark
 that it is built in a systematic structural way, one pNet node
@@
 \label{section:op-semantics}
+
+\QIN{[How about reduce the example of OT? But we still need keep the proof tree example.]}
 
@@
 
-Running our algorithm for our LOTOS example yields 30 open
-transitions, out of which 25 are detected unsatisfiable by Z3, so we
-get only 5 results left; the resulting open automaton is shown in
-Fig. ~\ref{schema:lotos-result}, we have drawn manually the open
-automaton obtained as the final result generated by algorithm.
-
-The $ot_1$ transition means that the actions of the process $P$ could
-be transmitted out, until $P$ performs a $\delta(x)$ and the value of
-$x$ is transmitted, through transition
-$ot_2$. The other 3 open transitions shows the behaviors of the
-process $Q$ while the $ot_3$ and $ot_4$ won't be performed as the
-controller has already set the value $s_0$ to 1 in the previous
-action.
-
-To sum up, from the pNet encoding LOTOS expression, inputed by the user, we
-generate the open transitions and prune the unsatisfiability
-automatically. The final result open transitions represent all the
-possible movements of the LOTOS example. They can exactly construct
-the open automaton for the given example.
+\QIN{[The fig is improved. A little change on the comments.]}
+
+\subsubsection{Result of LOTOS example}
+
+\QIN{
+yields 30 open
+transitions, out of which 27 are detected unsatisfiable by Z3, we
+get only 3 results left; the resulting open automaton is shown in
+Fig. ~\ref{schema:lotos-result}, together with its open transitions.
+}
+
+\QIN{
+The final result open transitions represent all the
+possible movements of the LOTOS example.
+What can be observed is always the actions of the process $P$ from the beginning, until $P$ performs a $\delta(x)$ and the value of
+$x$ is transmitted to the $acc(x);Q$ giving out a silent action. Such behavior is performed by the $ot_1$ and $ot_2$. 
+Then it keeps presenting the behavior of $Q$. $ot_3$ has showed that. 
+%The $ot_1$ transition means that the actions of the process $P$ could
+%be transmitted out, until $P$ performs a $\delta(x)$ and the value of
+%$x$ is transmitted, through transition
+%$ot_2$. The other 3 open transitions shows the behaviors of the
+%process $Q$ while the $ot_3$ and $ot_4$ won't be performed as the
+%controller has already set the value $s_0$ to 1 in the previous
+%action. 
+}
 
@@
 $\begin{array}{@{}r@{}l@{}}
-    ot_1  = &\openrule{\{0 \xrightarrow{l}_{C_1} 0\}, ~~\{\xrightarrow{hb_{11}}_P\}, ~~[s_0=0 \!\land\! hb_{11}=a_1 \!\land\! a_1\neq \delta(x) \!\land\! v_1=hb_{11}]}
+    ot_1  = &\openrule{\{0 \xrightarrow{l}_{C_1} 0\}, ~~\{\xrightarrow{hb_{1}}_P\}, ~~[s_0=0 \!\land\! hb_{1} \neq \delta(x) \!\land\! v_1=hb_{1}]}
     {\ostate{00} \xrightarrow{v_1} \ostate{00}}\\
@@
 $\begin{array}{@{}r@{}l@{}}
-    ot_2  = &\openrule{\{0 \xrightarrow{\delta}_{C_1} 0, 0 \xrightarrow{acc(x)}_{C_2} 1\}, ~~\{\xrightarrow{hb_{12}}_P\}, ~~[s_0=0 \!\land\!
-hb_{12}=\delta(x) \!\land\!
+    ot_2  = &\openrule{\{0 \xrightarrow{\delta}_{C_1} 0, 0 \xrightarrow{acc(x)}_{C_2} 1\}, ~~\{\xrightarrow{hb_{2}}_P\}, ~~[s_0=0 \!\land\!
+hb_{2}=\delta(x) \!\land\!
 v_2=\underline{\delta(x)}], ~~\{s_0 \xleftarrow{} 1\}}
@@
   $\begin{array}{@{}r@{}l@{}}
-    ot_3  = &\openrule{\{0 \xrightarrow{l}_{C_1} 0\}, ~~\{\xrightarrow{hb_{13}}_P\}, ~~[s_0=0 \!\land\! hb_{13}=a_1 \!\land\! a_1\neq \delta(x) \!\land\! v_3=a_1]}
+    ot_3  = &\openrule{\{0 \xrightarrow{r}_{C_1} 0, 1 \xrightarrow{q}_{C_2} 1\}, ~~\{\xrightarrow{hb_{3}}_Q\}, ~~[s_0=1 \!\land\! hb_{3} \neq acc(x) \!\land\! v_3=hb_{3}]}
     {\ostate{01} \xrightarrow{v_3} \ostate{01}}\\
@@
 
-$\begin{array}{@{}r@{}l@{}}
-    ot_4  = &\openrule{\{0 \xrightarrow{\delta}_{C_1} 0, 1 \xrightarrow{acc(x)}_{C_2} 1\}, ~~\{\xrightarrow{hb_{14}}_P\}, ~~[s_0=0 \!\land\!
-hb_{14}=\delta(x) \!\land\!
-v_4=\underline{\delta(x)}], ~~\{s_0 \xleftarrow{} 1\}}
-    {\ostate{01} \xrightarrow{v_5} \ostate{01}}\\
-  \end{array}$
-
-  $\begin{array}{@{}r@{}l@{}}
-    ot_5  = &\openrule{\{0 \xrightarrow{r}_{C_1} 0, 1 \xrightarrow{q}_{C_2} 1\}, ~~\{\xrightarrow{hb_{15}}_Q\}, ~~[s_0=1 \!\land\! hb_{15}=a_2 \!\land\! a_2\neq acc(x) \!\land\! v_5=a_2]}
-    {\ostate{01} \xrightarrow{v_5} \ostate{01}}\\
-  \end{array}$
-
 \caption{The open automaton of the LOTOS formula}  \label{schema:lotos-result}
 \end{figure}
+
+\subsubsection{Result of CCS example}
+\QIN{
+also can present all the possible behavior of that CCS formula with 16 open
+transitions in Fig. ~\ref{schema:ccs-result}, here we omitted the details of open transitions. 
+In this example, there are 32 more transitions detected unsatisfiable by Z3.
+}
+\begin{figure}[h]
+  \centerline{\includegraphics[width=5cm]{XFIG/CCSresult}}
+\caption{The open automaton of the CCS parallel formula}  \label{schema:ccs-result}
+\end{figure}
+
+\QIN{
+To sum up, from the pNets encoding the formulas of given algebra, which inputed by the user, we can exactly construct
+the open automaton for them. 
+}
 
@@
 induction. Also, we need more evidence that dealing with more complex
-action algebras, that would involve axiomatizing their dat structures
+action algebras, that would involve axiomatizing their data structures
 into Z3 theories, will indeed allow us to decide validity of

### 2017-06-19 2017-Xudong-SMT/submit-ICTAC2017.tex
Eric: todos from todays skype

@@
 
+\TODO{[ERIC] rewrite in stronger terms}
 \QIN{
@@
 
-\QIN{[We haven't used the input variables in this paper, we can remove them.]}
+\TODO{[We haven't used the input variables in this paper, we can remove them.]: NO, first see what we use to explain CCS use-case, then leave only a short definition of what we need}
 \QIN{[To be able to reason about the data flow between pLTSs, we
@@
 
+\TODO{Relate to the algorithm, or even move to section 5}
 When building an Open Automaton as the semantics of a pNet, its
@@
 
+\TODO{To be move  by Xudong}
+
 \subsection{Presentation of algebra}
@@
 
+\TODO{To be move / replace by Xudong}
 \subsection{Computing and using open automata}
@@
 \end{alg}
+
+\TODO{ERIC: after we move / replace Algoriithm 1, this will not make sense any longer. I will replace it with a more informal paragraph, in section 5}
 
@@
 \subsection{Combining and Matching using TR2}
+\TODO{Xudong: move here a (new version) of the alogorithm loplevel sketch}
 
@@
 
+\TODO{ERIC: reduce}
 We use a brute-force method to generate all the possible open

### 2017-06-19 2017-Xudong-SMT/submit-ICTAC2017.tex
Complete a part of the TODO.
Add the CCS example and result explanation.
Move the 4.1 and 4.2 to the Section 5. Stress that the real implementation has more stuff than the sketch.

@@
 synchronization structures in distributed or parallel languages.
-In this paper, we use an example inspired from Lotos, to illustrate
+
+In this paper, we use an example inspired from LOTOS, to illustrate
 the main features of pNets and the way we deal with them in the symbolic
 semantics, and in the satisfiability checking. 
+\QIN{
+Meanwhile, 
+the formula using operators from CCS can also be encoded into a pNet and 
+conducted with the same things.
+}
+
+\subsection{LOTOS Formula Example}
 
@@
 
+\subsection{CCS Parallel Example}
+
+\begin{figure}[h]
+  \centerline{\includegraphics[width=10cm]{XFIG/CCS1.eps}}
+  \caption{pNet encodings for the CCS expression}  \label{schema:ccs-pnet}
+\end{figure}
+
+\QIN{
+This CCS expression composing two operators, parallel and prefix. 
+It is easy to recognize that the pNets $PN2$ and $PN3$ are similar to 
+the sub-pNet in the LOTOS example in their structure and synchronization vectors. 
+That is because they are the operators conduct a similar behavior from different algebras.
+}
+
+\QIN{
+To present the parallel property, we have defined a set of synchronization vectors composing 
+two subnets. We use the notation from the CCS to present the emit and receive action. 
+The input variables $v_1$, $v_2$ are the data transmitting between two components, 
+showing its value-passing behavior.
+}
+
 It should be easy to see that this pNet system encodes properly the
-behavioral semantics of the corresponding Lotos expression. We remark
+behavioral semantics of the corresponding algebra expression. We remark
 that it is built in a systematic structural way, one pNet node
-encoding each Lotos operator. It is parameterized both at the level of
+encoding each operator. It is parameterized both at the level of
 actions variables (occurring within the controllers and the
@@
 
-\subsection{Presentation of algebra}
-One of the important goal of the Open pNet framework is to provide us
-with a model able to express the semantics of many different algebras
-or languages. In particular, as we have seen in section
-\ref{section:pnets}, the \emph{term algebra} used to express the
-action expressions and the data in their parameters is left open in
-the pNet formalization.
-
-So, for a given language, we now need to specify its data and action
-domains, giving them an abstract syntax (sorts, constructors, operators,
-and predicates). We call this a \emph{Presentation}.
-We also define a concrete syntax, that will be used for
-pretty-printing, but also for translating the presentation, and the
-predicates, into Z3 syntax (we shall detail this translation in
-section \ref{section:pruning}).
-
-An algebra presentation contains:
-\begin{itemize}
-	\item Sorts: Constants sets of the algebra or types of the data
-          and actions. In every presentation, sorts for integer and
-          boolean are implicitly declared.  There \emph{must} be one sort for actions, and eventually 
-several others for the types of data parameters. In the LOTOS example,
-we have the $Action$ sort: $\OTvar{Action = } \{ l, \delta, r, p, q, acc \} .$
-
-	\item Operators: Operators used to construct action
-          expressions (including their data parameters); they are
-          constructors of data and action sorts, but also predicates
-          over these objects. For instance, in our LOTOS example, we
-          could have two constructor functions ``$DELTA$'' and ``$ACC$''
-          to construct the action expression $\delta(x)$ and $acc(x)$, declared as:
-          $\OTvar{DELTA:}\OTvar{< Data >} \rightarrow \OTvar{Action .}$
-        \item Constants: The satisfiability solver need to know which
-          actions in the pLTS behaviors are constants (like the $l$, $\delta$, 
-          $r$ of the controllers in running example). 
-          For a given pNet system, a sort $Action$ will include all
-          these constants.
-\end{itemize}
+%\subsection{Presentation of algebra}
+%One of the important goal of the Open pNet framework is to provide us
+%with a model able to express the semantics of many different algebras
+%or languages. In particular, as we have seen in section
+%\ref{section:pnets}, the \emph{term algebra} used to express the
+%action expressions and the data in their parameters is left open in
+%the pNet formalization.
+%
+%So, for a given language, we now need to specify its data and action
+%domains, giving them an abstract syntax (sorts, constructors, operators,
+%and predicates). We call this a \emph{Presentation}.
+%We also define a concrete syntax, that will be used for
+%pretty-printing, but also for translating the presentation, and the
+%predicates, into Z3 syntax (we shall detail this translation in
+%section \ref{section:pruning}).
+%
+%An algebra presentation contains:
+%\begin{itemize}
+%	\item Sorts: Constants sets of the algebra or types of the data
+%          and actions. In every presentation, sorts for integer and
+%          boolean are implicitly declared.  There \emph{must} be one sort for actions, and eventually 
+%several others for the types of data parameters. In the LOTOS example,
+%we have the $Action$ sort: $\OTvar{Action = } \{ l, \delta, r, p, q, acc \} .$
+%
+%	\item Operators: Operators used to construct action
+%          expressions (including their data parameters); they are
+%          constructors of data and action sorts, but also predicates
+%          over these objects. For instance, in our LOTOS example, we
+%          could have two constructor functions ``$DELTA$'' and ``$ACC$''
+%          to construct the action expression $\delta(x)$ and $acc(x)$, declared as:
+%          $\OTvar{DELTA:}\OTvar{< Data >} \rightarrow \OTvar{Action .}$
+%        \item Constants: The satisfiability solver need to know which
+%          actions in the pLTS behaviors are constants (like the $l$, $\delta$, 
+%          $r$ of the controllers in running example). 
+%          For a given pNet system, a sort $Action$ will include all
+%          these constants.
+%\end{itemize}
 
@@
 \TODO{To be move / replace by Xudong}
-\subsection{Computing and using open automata}
-In this section we present an algorithm to construct the open
-automaton representing the behavior of an open pNet, and show
-under which conditions this automaton is finite.
-
-\begin{alg}[behavioral semantics of open pNets: Sketch]
-This is a standard residual algorithm over a set of open-automaton
-states, but where transitions are open transitions
-constructively ``proven'' by deduction trees.
-
-1) Start with a set of unexplored states containing the initial state
-of the automaton, and an empty set of explored states.
-
-2) While there are unexplored states:
-
-2a) pick one state from the unexplored set and add it to the explored
-set. From this state
-build all possible deduction trees by application of the structural
-rules Tr1 and Tr2, using all applicable combinations
-of synchronization vectors.
-
-2b) For each deduction trees, extract the resulting
-open-transition.
-Its predicate is checked (using Z3) for  satisfiability. If it is
-unsatisfiable, the resulting OT is discarded. This will minimize the
-number of resulting transitions.
-
-2c) For each open-transition,  add the transition in the outgoing transitions of
-the current state, and add the
-resulting state in the unexplored set if it is not already in the
-explored set.
-
-3) Finally a reachability check could potentially
-prune the state space.
-
-\end{alg}
+%\subsection{Computing and using open automata}
+%In this section we present an algorithm to construct the open
+%automaton representing the behavior of an open pNet, and show
+%under which conditions this automaton is finite.
+%
+%\begin{alg}[behavioral semantics of open pNets: Sketch]
+%This is a standard residual algorithm over a set of open-automaton
+%states, but where transitions are open transitions
+%constructively ``proven'' by deduction trees.
+%
+%1) Start with a set of unexplored states containing the initial state
+%of the automaton, and an empty set of explored states.
+%
+%2) While there are unexplored states:
+%
+%2a) pick one state from the unexplored set and add it to the explored
+%set. From this state
+%build all possible deduction trees by application of the structural
+%rules Tr1 and Tr2, using all applicable combinations
+%of synchronization vectors.
+%
+%2b) For each deduction trees, extract the resulting
+%open-transition.
+%Its predicate is checked (using Z3) for  satisfiability. If it is
+%unsatisfiable, the resulting OT is discarded. This will minimize the
+%number of resulting transitions. 
+%
+%2c) For each open-transition,  add the transition in the outgoing transitions of
+%the current state, and add the
+%resulting state in the unexplored set if it is not already in the
+%explored set.
+%
+%3) Finally a reachability check could potentially
+%prune the state space.
+%
+%\end{alg}
 
@@
 \TODO{Xudong: move here a (new version) of the alogorithm loplevel sketch}
+\QIN{
+In previous work, we already have a sketch for computing the open automaton.
+}
+
+\QIN{
+1) Start with the initial state of the automaton. 
+}
+
+\QIN{
+2) Apply Tr1 and Tr2 to deduct all the possible open transitions. Use SMT solver to prune the 
+unsatisfiable transitions. Recursively conduct this step with the target state of the transitions 
+until all the global states are explored.
+}
+
+\QIN{
+3) Finally a reachability check could potentially prune the state space.
+}
+
+\QIN{
+The detail about the application of the Tr1 and Tr2 have not considered in the sketch, but it is an  
+important part in the implementation of open transition generation. Each time we apply Tr1, there is not too much predicate terms, so do the other parameters, needed 
+to be generated. When it comes to applying Tr2, the computation becomes complicated because it doing some composition of the subnets.
+}
 
@@
 
+\paragraph{Presentation of algebra}
+\QIN{
+Open pNet framework provides us
+with a model able to express the semantics of many different algebras
+or languages. In particular, as we have seen in section
+\ref{section:pnets}, the \emph{term algebra} used to express the
+action expressions and the data in their parameters is left open in
+the pNet formalization.
+}
+
+\QIN{
+So, for a given language, we now need to specify its data and action
+domains, giving them an abstract syntax (sorts, constructors, operators,
+and predicates). We call this a \emph{Presentation}.
+We also define a concrete syntax, that will be used for
+pretty-printing, but also for translating the presentation, and the
+predicates, into Z3 syntax.
+}
+
+\QIN{
+An algebra presentation contains:
+}
+
+\begin{itemize}
+	\item Sorts: Constants sets of the algebra or types of the data
+          and actions. In every presentation, sorts for integer and
+          boolean are implicitly declared.  There \emph{must} be one sort for actions, and eventually 
+several others for the types of data parameters. In the LOTOS example,
+we have the $Action$ sort: $\OTvar{Action = } \{ l, \delta, r, p, q, acc \} .$
+
+	\item Operators: Operators used to construct action
+          expressions (including their data parameters); they are
+          constructors of data and action sorts, but also predicates
+          over these objects. For instance, in our LOTOS example, we
+          could have two constructor functions ``$DELTA$'' and ``$ACC$''
+          to construct the action expression $\delta(x)$ and $acc(x)$, declared as:
+          $\OTvar{DELTA:}\OTvar{< Data >} \rightarrow \OTvar{Action .}$
+        \item Constants: The satisfiability solver need to know which
+          actions in the pLTS behaviors are constants (like the $l$, $\delta$, 
+          $r$ of the controllers in running example). 
+          For a given pNet system, a sort $Action$ will include all
+          these constants.
+\end{itemize}
+
 \paragraph{Interaction with Z3}
@@
 }
+
+\QIN{
+Here we only show one of the result transitions. It presents the value-passing between $a.P$ and $b.Q$ and they are synchronized then
+give out an silent action $\tau$, process $P$ and $Q$ should not work in this case.
+}
+
 \begin{figure}[h]
   \centerline{\includegraphics[width=5cm]{XFIG/CCSresult}}
+
+  $\begin{array}{@{}r@{}l@{}}
+    ot_1  = &\openrule{\{0 \xrightarrow{a}_{C_1} 1, 0 \xrightarrow{b}_{C_2} 1\}, ~~a=!ch_{11}(v_{11}) \!\land\! b=?ch_{11}(v_{11}) \!\land\! a\neq l \!\land\! b\neq r\!\land\! v_1=\tau}
+    {\ostate{00} \xrightarrow{v_1} \ostate{11}}\\
+  \end{array}$
+
 \caption{The open automaton of the CCS parallel formula}  \label{schema:ccs-result}

### 2017-06-20 2017-Xudong-SMT/submit-ICTAC2017.tex
Add more comments about why using SMT(Z3).
In Section 5.4.

@@
 \QIN{
-This CCS expression composing two operators, parallel and prefix. 
-It is easy to recognize that the pNets $PN2$ and $PN3$ are similar to 
+This CCS expression composing two operators, parallel and prefix. In Fig.~\ref{schema:ccs-pnet}, 
+it is easy to recognize that the pNets $PN2$ and $PN3$ are similar to 
 the sub-pNet in the LOTOS example in their structure and synchronization vectors. 
@@
 may depend on the specific theory of the action algebra. 
-We choose to use the SMT solver Z3 as the checker engine, considering
+\QIN{
+So we cannot do it on our own pNet API.
+}
+
+\QIN{
+In our implementation, we use the SMT solver to check the predicate of the result open transitions, 
+it will return whether the predicate is satisfiable or not.
+}
+We choose the SMT solver Z3 as the checker engine, considering
 the predicates may contain the expression 

### 2017-06-20 2017-Xudong-SMT/submit-ICTAC2017.tex
remove notion of input variable

--- 2017-06-19 2017-Xudong-SMT/submit-ICTAC2017.tex
@@
 naturally action terms will use data expressions as sub-terms.
-
-\TODO{[We haven't used the input variables in this paper, we can remove them.]: NO, first see what we use to explain CCS use-case, then leave only a short definition of what we need}
-\QIN{[To be able to reason about the data flow between pLTSs, we
-distinguish \emph{input variables} of the form $?x$ within terms; the function
-$\vars(t)$ identifies the set of variables in a term
-$t\in\AlgT$, and $iv(t)$ returns its input variables.]}
+The function $\vars(t)$ identifies the set of variables in a term
+$t\in\AlgT$.
+
+%% \TODO{[We haven't used the input variables in this paper, we can remove them.]: NO, first see what we use to explain CCS use-case, then leave only a short definition of what we need}
+%% \QIN{[To be able to reason about the data flow between pLTSs, we
+%% distinguish \emph{input variables} of the form $?x$ within terms; the function
+%% $\vars(t)$ identifies the set of variables in a term
+%% $t\in\AlgT$, and $iv(t)$ returns its input variables.]}
 
@@
 %variable values from one state to the other can be done by explicit assignment.
-\QIN{
+
 Each state has its set of variables called state variables.
@@
 A global state variable of a pLTS is a variable $x$ satisfying $\forall s\!\in\! S .\, x\!\in\! \vars(s)$.
-}
 
@@
 %\]
-\QIN{
-[The input variables in an action term are those marked with a
-$\symb{?}$.
-We additionally suppose that each input variable does not
-appear somewhere else in the same action term:
-$p_i=?x\Rightarrow\forall j\neq i.\, x\notin \vars(p_j)$]}
+
+%% \QIN{
+%% [The input variables in an action term are those marked with a
+%% $\symb{?}$.
+%% We additionally suppose that each input variable does not
+%% appear somewhere else in the same action term:
+%% $p_i=?x\Rightarrow\forall j\neq i.\, x\notin \vars(p_j)$]}
 
@@
 If 
+%% $s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
+%% 		J}\rangle} s'\in \to $ then $\iv(\alpha)\!\subseteq\! \vars(s')$, 
+%% 		$\vars(\alpha)\backslash \iv(\alpha)\!\subseteq\! \vars(s)$, 
+%% 		$\vars(e_b)\!\subseteq\! \vars(s')$, and
+%% 		$\forall j\!\in\! J .\,\vars(e_j)\!\subseteq\! \vars(s)\land 
+%% x_j\!\in\!\vars(s')$.
+
 $s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
-		J}\rangle} s'\in \to $ then $\iv(\alpha)\!\subseteq\! \vars(s')$, 
-		$\vars(\alpha)\backslash \iv(\alpha)\!\subseteq\! \vars(s)$, 
+		J}\rangle} s'\in \to $ then 
+		$\vars(\alpha)\!\subseteq\! \vars(s)$, 
 		$\vars(e_b)\!\subseteq\! \vars(s')$, and
 		$\forall j\!\in\! J .\,\vars(e_j)\!\subseteq\! \vars(s)\land 
-		x_j\!\in\!\vars(s')$. %,  and $s= s'\Rightarrow J=\emptyset$. 
+x_j\!\in\!\vars(s')$.
+
+%,  and $s= s'\Rightarrow J=\emptyset$. 
 \item[$\bullet$]
@@
 exposes a single resulting global action.
-Actions involved at the pNet level (in the synchronization vectors) do
-not need to distinguish between input and output
-variables. Action terms for pNets are defined as follows:
+% Actions involved at the pNet level (in the synchronization vectors) do
+% not need to distinguish between input and output
+% variables.
+Action terms for pNets are defined as follows:
 \[\begin{array}[l]{rcl@{\quad}l}
@@
 two subnets. We use the notation from the CCS to present the emit and receive action. 
-The input variables $v_1$, $v_2$ are the data transmitting between two components, 
+The variables $v_1$, $v_2$ are the data transmitting between two components, 
 showing its value-passing behavior.

### 2017-06-20 2017-Xudong-SMT/submit-ICTAC2017.tex
rewritten intro

@@
 The pNet model was developed in a series of
-papers~\cite{HMZ:PDP15,henrio:Forte2016} and some examples have been
+papers~\cite{HMZ:PDP15,henrio:Forte2016} in which many examples have been
 introduced showing its ability to encode the operators from some
-other algebras or  program skeletons. The operational semantic of the open pNet has
-already been defined, but we only had a sketch about how to compute it and
-had no implementation. This operational semantic is defined as an
+other algebras or  program skeletons.
+The operational semantic of an (open) pNet is defined as an
 Open Automaton in which Open Transitions contain logical predicates
 expressing the relations between the behavior of the holes, and the
-global behavior of the system.
-
-Computing the open transitions from the composition of pNet is the
-main part of the algorithm and needs to satisfy the constraints expressed as
-the rules of the operational semantics.
-Computing open automata by hand is complicated and error prone.
-
-\TODO{[ERIC] rewrite in stronger terms}
-\QIN{
-And the algorithm published in \cite{henrio:Forte2016} was not the algorithm we are using
-so far, which is more precise, defining more details of the algorithm, such as the application of 
-the rules on the detection of open transitions and the management of the "data" expressions. 
-}
-
-%And
-%the algorithm published in \cite{henrio:Forte2016} was not precise
-%enough for an implementation. 
-Our first goal was then to refine the
-algorithm, and implement it in a tool.
+global behavior of the system. In the previous publication,
+only a sketch of a procedure allowing to compute this semantics was
+presented, together with a proof of finiteness of the open automaton, under
+reasonable hypotheses on the pNet structure.
+
+Implementing this semantics raised several challenges, in order:
+\begin{itemize}
+  \item To get a tool that could be applied to pNets representing
+    various languages, in particular various actions algebras,
+    with their specific decision theories.
+  \item To separate clearly the algorithmic part, as a residual
+      algorithm generating the transitions of the open automaton from
+      combination of all possible (symbolic) behaviors on one hand; from the
+      symbolic reasonning part, specificaly here checking the
+      satisfiability of the predicates generated by our algorithm,
+      that we delegate to a generic SMT engine, on the other hand.
+  \item To build a prototype and validate the approach on our basic
+    case-studies, and understand the efficiency of the interaction
+    with the SMT solver.
+\end{itemize}
+
 In the long goal, we want to be able to check the equivalence between
-pNets. The equivalence between pNets is "FH-bisimulation" taking the
+open systems encoded as pNets. The equivalence between pNets is
+"FH-bisimulation" taking the 
 predicate of the open transitions into account each time matching such
-open transitions. In our long-term goals, the final target is to check
-the property of open systems.
-
-This paper presents our open automaton computing algorithm and its
-implementation using the pNet API. Comparing the result of the algorithm with
-the manual result on our running examples shows that the algorithm
-works properly in computing the pNet semantics. The
-algorithm contains the method computing the open transitions composing
-the transitions from the subnets according to several defined rules
-the open transitions need to satisfy. These results are not the final
-results in fact, because they contain some unsatisfiable results we need
-to eliminate. To eliminate those unsatisfiability, we interact with an
-automatic theorem prover for satisfiability checking.
+open transitions. We foresee that the interplay with the SMT solver
+that we use here for satisfiability of open transitions will be
+similar with what we need to prove (symbolic) equivalence between open
+transitions.
+
+%% This paper presents our open automaton computing algorithm and its
+%% implementation using the pNet API from the VerCors platform.
+%% Comparing
+%% the result of the algorithm with 
+%% the manual result on our running examples shows that the algorithm
+%% works properly in computing the pNet semantics.
+%% The
+%% algorithm contains the method computing the open transitions composing
+%% the transitions from the subnets according to several defined rules
+%% the open transitions need to satisfy. These results are not the final
+%% results in fact, because they contain some unsatisfiable results we need
+%% to eliminate. To eliminate those unsatisfiability, we interact with an
+%% automatic theorem prover for satisfiability checking.
 
@@
 \begin{itemize}
-\item We have refined the open automaton generation algorithm, to make
-  it implementable, and we implemented a full working prototype, within the
+\item We have defined the open automaton generation algorithm, and we
+  implemented a full working prototype, within the 
   VerCors platform. In the process, we had to improve significantly the
-  semantics rules, and add features in the algorithm to deal the full
+  semantics rules from~\cite{henrio:Forte2016}, and add features in
+  the algorithm to deal the full 
   model, including management of variables and assignments.
@@
     generated by the algorithm.
-\item We validated the whole approach on a small use-case covering all
+\item We validated the whole approach on small use-cases covering all
       important features of the model.

### 2017-06-20 2017-Xudong-SMT/submit-ICTAC2017.tex
Section 3 et 4

@@
 \newcommand{\Pred}{\symb{Pred}}
+\newcommand{\MkPred}{\symb{MkPred}}
 \newcommand{\Post}{\symb{Post}}
@@
 In Fig.~\ref{schema:lotos-pnet}, we show the encoding of the formula using pNets. 
-
 This pNet is composed of: a toplevel node PN1 encoding the Enable
@@
 
-Now look more specifically on the top pNet node PN1. In addition to
+Now consider the top pNet node PN1. In addition to
 its controller it has 2 sub-pNets: the hole P and the sub-pNet PN2.
-Three synchronization vectors are defining the possible
-synchronizations between the actions of the subnets.
- The first
-vector, transmitting an action $a_1$ of P, can only occur if $a_1$ is not
-a $\delta$, the vector concrete syntax is typically ``$< l, a_1 , \_ >
--> a_1$'', in which ``$\_$'' means that the corresponding subnet is
+Three synchronization vectors define the possible
+synchronizations between the actions of its subnets.
+The first vector ``$< l, a_1 , \_ > -> a_1$'', transmitting an action
+$a_1$ of P, can only occur if $a_1$ is not  
+a $\delta$, here ``$\_$'' means that the corresponding subnet is
 not involved in this synchronization, and the ``l'' action is related
@@
 available only when the state variable $s_0$ is equal to 0.
-The second vector composes the
-actions from the subnets and gives out a synchronized action
-$\underline{\delta(x)}$, where the underlined action stands for an
-internal (already synchronized) action, that cannot be further
-synchronized at upper levels. Synchronized action is a straightforward
+The second synchronisation vector composes an
+action $\delta(x)$ from $P$ with an $acc(x)$ from $Q$, transmitting a
+value $x$ before $Q$ takes the control; 
+The vector result $\underline{\delta(x)}$ is an
+internal action, called ``synchronized'' that cannot be further
+synchronized at upper levels. Synchronized actions is a straightforward
 generalization of the notion of internal actions, that will be
-convenient for observing internal events during model-checking. Here
-the transition occurs only when process
-$P$ performs a $\delta(x)$ action, transferring the control to $Q$,
-and sending a value $x$ at the same time. This value must be
-``accepted''  through an $acc(x)$ action before $Q$ takes the
-control. The last vector acts as the first one, but transmitting the
-action $a_2$ of Q.  
+convenient for observing internal events during model-checking.
+The last vector acts is to the first one.  
 Similarly the node PN2 has two synchronization vectors to encode
 the behavior of the Prefix operator.
+
+It should be easy to see that this pNet system encodes properly the
+behavioral semantics of the corresponding algebra expression. We remark
+that it is built in a systematic structural way, one pNet node
+encoding each operator.
+%% It is parameterized both at the level of
+%% actions variables (occurring within the controllers and the
+%% synchronization vectors), and at the level of process parameters
+%% (holes).
+
+\TODO{I'm thinking about moving this second example to section 5...}
 
@@
 
-It should be easy to see that this pNet system encodes properly the
-behavioral semantics of the corresponding algebra expression. We remark
-that it is built in a systematic structural way, one pNet node
-encoding each operator. It is parameterized both at the level of
-actions variables (occurring within the controllers and the
-synchronization vectors), and at the level of process parameters
-(holes).
-
 \section{Operational Semantics for Open pNets}
@@
 
-\QIN{[How about reduce the example of OT? But we still need keep the proof tree example.]}
-
 The semantics of open pNets will be defined  as an open automaton. An open
-automaton is an automaton where each transition composes transitions of several LTSs with
-action of some holes, the transition occurs if some predicates hold, and can involve a 
-set of state modifications.
+automaton is an automaton where each transition composes transitions
+of several LTSs with the
+actions of some holes; the transition occurs if some predicates hold,
+and can involve a set of state modifications.
 
@@
         sort $Sort_j$. \Pred\ is a predicate
-	over the different variables of the
-	terms, labels, and states $s_i$, $b_j$, $s$, $v$. \Post\ is a set of equations that 
-	hold \emph{after the open transition}, they are represented as a substitution of the 
-	form $\{x_k\gets e_k\}^{k\in K}$ 
-	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
-	variables of the open transition.
+	over the variables of the terms, labels, and states $s_i$,
+        $b_j$, $s$, $v$. \Post\ is a set of equations that  
+	hold \emph{after the open transition}, represented as a
+        substitution $\{x_k\gets e_k\}^{k\in K}$  
+	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are
+        expressions over the other variables of the open transition.
 \end{definition}
@@
 
-\TODO{Relate to the algorithm, or even move to section 5}
+% \TODO{Relate to the algorithm, or even move to section 5}
 When building an Open Automaton as the semantics of a pNet, its
@@
 $\mylangle\overline{\pNet},\overline{S},\symb{SV}_k^{k\in K} \myrangle$
-be a pNet. Consider a synchronization vector $SV_k$, for $k\in K$. We define a
-predicate $\Pred$ relating
+be a pNet. Consider a synchronization vector $SV_k$, for $k\in K$. We build a
+predicate $\MkPred$ relating
 the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
-\[\Pred(SV_k, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow
+\[\MkPred(SV_k, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow
 \begin{array}{l}
@@
 
-This definition is not constructive but it is easy to build the predicate constructively
-by brute-force unification of the sub-pNets
+This definition is not constructive but it is easy to build the
+predicate constructively by brute-force unification of the sub-pNets
 actions with the corresponding vector actions, possibly followed by a simplification
@@
 
-%\QIN{[ change the example OT here ]}
 \begin{example}\emph{An open-transition.}
@@
 controllers and 2 holes. We will show its full open Automaton in
-section \ref{section:full-result}. We give one of its transition here:
+section \ref{section:full-result}. We give one of its transitions here:
 
@@
 
-The semantic of the open pNets is already defined as an open automaton in \cite{henrio:Forte2016} using open transitions to present the transitions of its global states.
+% The semantic of the open pNets is already defined as an open automaton
+% in \cite{henrio:Forte2016} using open transitions to present the
+% transitions of its global states.
+
 \begin{definition}[Operational semantics of open pNets]
@@
 
-  The second rule deals with pNet nodes: for each possible
+  The second rule ({\bf Tr2}) deals with pNet nodes: for each possible
   synchronization vector applicable to the rule subject, the premisses
@@
   Leaves, $L_k$ the index set of the leaves of one subnet, so all $L_k$
-  are disjoint subsets of $L$. Thus the states in the open transitions,
-  at each level, are tuples including states of all the
-  leaves of the pNet, not only those involved in the chosen
-  synchronization vector.
+  are disjoint subsets of $L$. % Thus the states in the open transitions,
+%   at each level, are tuples including states of all the
+%   leaves of the pNet, not only those involved in the chosen
+%  synchronization vector.
 
@@
       \Pred = \bigwedge_{m\in I_k}\!\! \Pred_m \land
-      \Pred(SV,v_m^{m\in I_k},b_j^{j\in J_k},v)\\
+      \MkPred(SV,v_m^{m\in I_k},b_j^{j\in J_k},v)\\
       \forall j\!\!\in\!\! J_k. {\tt 
@@
 
-\TODO{To be move  by Xudong}
+% \TODO{To be move  by Xudong}
 
@@
 
-\TODO{To be move / replace by Xudong}
+% \TODO{To be move / replace by Xudong}
+
 %\subsection{Computing and using open automata}
@@
 
-To have some practical interest, it is important to know when this
-algorithm terminates. The following theorem shows that an open-pNet
-with finite synchronization sets, finitely many leaves and
-holes, and each pLTS at leaves having a finite number of states and
-(symbolic) transitions, has a finite automaton. The proof can be found
-in \cite{henrio:Forte2016}.
-
-\begin{theorem}[Finiteness of open-automata.]\\
-Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
-  J}$, if the sets $L$ and $J$ are finite, if the synchronization vectors of all pNets 
-  included in  $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ 
-  are finite, and if
-$\forall i \in L.\, finite{(states(pLTS_i))} \text{ and } pLTS_i$
-has a finite number of state variables, then Algorithm 1 terminates
-and produces an open automaton 
-$\mathcal{T}$ with finitely many states and transitions.
+%% To have some practical interest, it is important to know when this
+%% algorithm terminates. The following theorem shows that an open-pNet
+%% with finite synchronization sets, finitely many leaves and
+%% holes, and each pLTS at leaves having a finite number of states and
+%% (symbolic) transitions, has a finite automaton. The proof can be found
+%% in \cite{henrio:Forte2016}.
+
+%% \begin{theorem}[Finiteness of open-automata.]\\
+%% Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
+%%   J}$, if the sets $L$ and $J$ are finite, if the synchronization vectors of all pNets 
+%%   included in  $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ 
+%%   are finite, and if
+%% $\forall i \in L.\, finite{(states(pLTS_i))} \text{ and } pLTS_i$
+%% has a finite number of state variables, then Algorithm 1 terminates
+%% and produces an open automaton 
+%% $\mathcal{T}$ with finitely many states and transitions.
 
@@
 %   \to finite{(\mathcal{T})}$$
-\end{theorem}
+% \end{theorem}
 

### 2017-06-20 2017-Xudong-SMT/submit-ICTAC2017.tex
section5.4

@@
 
-\TODO{ERIC: reduce}
+\begin{figure}[h]
+%$\begin{array}{@{}r@{}l@{}}
+%%{s0---a-->s1},   {---:hb:15:2-->},   (:ra:15:2 = act:sva:1:3)/\(:ra:152:1 = l)/\(a = :ra:152:1)/\(l!= a)/\(:hb:15:2 = y:sva:15:2)/\(:ra:15:2 = y:sva:15:2)/\(y:sva:15:2 != l)/\(:ra:1:3 = act:sva:1:3)
+%    ot  = &\openrule{\{0 \xrightarrow{a} 1\}, ~~\{\xrightarrow{:hb:15:2}\}, ~~:ra:15:2=act:sva:1:3 \\
+%    \OTland:ra:152:1=l \OTland a=:ra:152:1 \OTland a \neq l \OTland :hb:15:2 = y:sva:15:2 \\
+%    \OTland :ra:15:2 = y:sva:15:2  \OTland y:sva:15:2 \neq l \OTland :ra:1:3 = act:sva:1:3}
+%    {\ostate{00} \xrightarrow{:ra:1:3} \ostate{10}}\\
+%  \end{array}$
+%\caption{One of the unsatisfiable open transitions in CCS running example}  \label{schema:unsat-ot}
+%\end{figure}
+
+%{s0---delta-->s0},   {---:hb_P:12:1-->},   (:ra:11:1=l)/\(delta=:ra:11:1)/\(var_s0=0)/\(:hb_P:12:1=a1:sva_SV0:1:1)/\(:ra:1:1=a1:sva_SV0:1:1)/\(a1:sva_SV0:1:1!=delta(x)),   {var_s0 := 1}
+$\begin{array}{@{}r@{}l@{}}
+    ot  = &\openrule{\{0 \xrightarrow{\delta} 0\}, ~~\{\xrightarrow{:hb:12:1}\}, ~~\OTvar{:ra:11:1}=l \OTland \delta=\OTvar{:ra:11:1} \OTland \OTvar{s0}=0 \\
+     \OTland \OTvar{:hb:12:1}=\OTvar{a1:sva:1:1} \OTland \OTvar{:ra:1:1}=\OTvar{a1:sva:1:1} \OTland \OTvar{a1:sva:1:1} \neq \delta(x), ~~\{\OTvar{s0} \leftarrow 1\}}
+    {\ostate{00} \xrightarrow{\OTvar{:ra:1:1}} \ostate{00}}\\
+  \end{array}$
+\caption{One of the unsatisfiable open transitions in LOTOS running example}  \label{schema:unsat-ot}
+\end{figure}
+
 We use a brute-force method to generate all the possible open
@@
 may depend on the specific theory of the action algebra. 
-\QIN{
-So we cannot do it on our own pNet API.
-}
-
-\QIN{
-In our implementation, we use the SMT solver to check the predicate of the result open transitions, 
+We use the SMT solver Z3 to check the predicate of the result open transitions, 
 it will return whether the predicate is satisfiable or not.
-}
-We choose the SMT solver Z3 as the checker engine, considering
-the predicates may contain the expression 
-using uninterpreted functions declared by users.
 The ``Modulo Theory'' part of SMT solvers is important here, so that
 the solver can use specific properties of each action algebra.
-
-\begin{figure}[t]
-%$\begin{array}{@{}r@{}l@{}}
-%%{s0---a-->s1},   {---:hb:15:2-->},   (:ra:15:2 = act:sva:1:3)/\(:ra:152:1 = l)/\(a = :ra:152:1)/\(l!= a)/\(:hb:15:2 = y:sva:15:2)/\(:ra:15:2 = y:sva:15:2)/\(y:sva:15:2 != l)/\(:ra:1:3 = act:sva:1:3)
-%    ot  = &\openrule{\{0 \xrightarrow{a} 1\}, ~~\{\xrightarrow{:hb:15:2}\}, ~~:ra:15:2=act:sva:1:3 \\
-%    \OTland:ra:152:1=l \OTland a=:ra:152:1 \OTland a \neq l \OTland :hb:15:2 = y:sva:15:2 \\
-%    \OTland :ra:15:2 = y:sva:15:2  \OTland y:sva:15:2 \neq l \OTland :ra:1:3 = act:sva:1:3}
-%    {\ostate{00} \xrightarrow{:ra:1:3} \ostate{10}}\\
-%  \end{array}$
-%\caption{One of the unsatisfiable open transitions in CCS running example}  \label{schema:unsat-ot}
-%\end{figure}
-
-%{s0---delta-->s0},   {---:hb_P:12:1-->},   (:ra:11:1=l)/\(delta=:ra:11:1)/\(var_s0=0)/\(:hb_P:12:1=a1:sva_SV0:1:1)/\(:ra:1:1=a1:sva_SV0:1:1)/\(a1:sva_SV0:1:1!=delta(x)),   {var_s0 := 1}
-$\begin{array}{@{}r@{}l@{}}
-    ot  = &\openrule{\{0 \xrightarrow{\delta} 0\}, ~~\{\xrightarrow{:hb:12:1}\}, ~~\OTvar{:ra:11:1}=l \OTland \delta=\OTvar{:ra:11:1} \OTland \OTvar{s0}=0 \\
-     \OTland \OTvar{:hb:12:1}=\OTvar{a1:sva:1:1} \OTland \OTvar{:ra:1:1}=\OTvar{a1:sva:1:1} \OTland \OTvar{a1:sva:1:1} \neq \delta(x), ~~\{\OTvar{s0} \leftarrow 1\}}
-    {\ostate{00} \xrightarrow{\OTvar{:ra:1:1}} \ostate{00}}\\
-  \end{array}$
-\caption{One of the unsatisfiable open transitions in LOTOS running example}  \label{schema:unsat-ot}
-\end{figure}
 
@@
 \paragraph{Presentation of algebra}
-\QIN{
-Open pNet framework provides us
-with a model able to express the semantics of many different algebras
-or languages. In particular, as we have seen in section
+
+%% Open pNet framework provides us
+%% with a model able to express the semantics of many different algebras
+%% or languages. In particular,
+As seen in section
 \ref{section:pnets}, the \emph{term algebra} used to express the
-action expressions and the data in their parameters is left open in
-the pNet formalization.
-}
-
-\QIN{
+action expressions and data parameters is left open in
+the pNet definition.
+
 So, for a given language, we now need to specify its data and action
@@
 pretty-printing, but also for translating the presentation, and the
-predicates, into Z3 syntax.
-}
-
-\QIN{
+predicates, into Z3 syntax (see the ``declare-datatypes'' statement in
+Fig~\ref{schema:smt-lib}).
+
 An algebra presentation contains:
-}
 
@@
 	\item Sorts: Constants sets of the algebra or types of the data
-          and actions. In every presentation, sorts for integer and
-          boolean are implicitly declared.  There \emph{must} be one sort for actions, and eventually 
-several others for the types of data parameters. In the LOTOS example,
-we have the $Action$ sort: $\OTvar{Action = } \{ l, \delta, r, p, q, acc \} .$
-
-	\item Operators: Operators used to construct action
-          expressions (including their data parameters); they are
-          constructors of data and action sorts, but also predicates
-          over these objects. For instance, in our LOTOS example, we
-          could have two constructor functions ``$DELTA$'' and ``$ACC$''
-          to construct the action expression $\delta(x)$ and $acc(x)$, declared as:
-          $\OTvar{DELTA:}\OTvar{< Data >} \rightarrow \OTvar{Action .}$
+          and actions (integer and boolean sort are implicitly
+          declared).  There \emph{must} be one sort for actions, and
+          eventually others for the types of data
+          parameters. In the LOTOS example, 
+          we have the $Action$ sort: $\OTvar{Action = } \{ l, \delta,
+          r, p, q, acc \} .$
+
+	\item Operators:
+          %Operators used to construct action expressions; they are
+          constructors and predicates for data and action sorts. For
+          instance, in our LOTOS example, we
+          have a generic action constructor ``$ACT$'', taking as
+          argument an action litteral and a data parameter, declared as:
+          $\OTvar{ACT:}\OTvar{< Action, Data >} \rightarrow \OTvar{Action.}$, 
         \item Constants: The satisfiability solver need to know which
@@
           $r$ of the controllers in running example). 
-          For a given pNet system, a sort $Action$ will include all
+          For a given pNet system, the sort $Action$ will include all
           these constants.
@@
 From inside our algorithm code, we submit satisfiability requests to
-Z3 using its JAVA API. In this article, to make the reading easier, we
-show the Z3 code fragments using its SMT-LIB input language. As an
+Z3 using its JAVA API. Here for readability, we
+show the Z3 code using its SMT-LIB input language. As an
 example in
-Fig~\ref{schema:smt-lib}, we show the input for checking the (unsatisfiable)
-transition of Fig.~\ref{schema:unsat-ot}.
-
-The input to Z3 contains the declaration of the LOTOS action algebra types
+Fig~\ref{schema:smt-lib}, we show the input for checking the
+transition of Fig.~\ref{schema:unsat-ot}. It contains the declaration
+of the LOTOS action algebra types 
 and constructors, then the declaration of variables, and finally the
 predicate to be checked, encoded as a set of assertions.
-Generally, some $datatypes$ are declared to input the sorts, while here
-we only declare one $datatypes$ named $Action$ to involve all the
-constant actions. Then we input the predicate of that open transition
-in two parts. The variables contained in the predicate are declared
-first, then the terms of predicate are inputed as $assertions$ one by
-one. The result "unsat" in the output is just what we expected.
+%% Generally, some $datatypes$ are declared to input the sorts, while here
+%% we only declare one $datatypes$ named $Action$ to involve all the
+%% constant actions. Then we input the predicate of this open transition
+%% in two parts: the variables contained in the predicate are declared
+%% first, then the terms of predicate are inputed as $assertions$ one by
+%% one. 
+The result "unsat" in the output is just what we expected.
 
@@
 The $functions$ can also be declared independently, it usually applies to functions returning integer or boolean, in the format like:\\
-\centerline{$\OTvar{(declare\text{-}fun\ ACT\ (Action\ Int)\ Action)}$}
+\centerline{$\OTvar{(declare\text{-}fun\ MAX\ (Int\ Int)\ Int)}$}
 
@@
 State-variable assignments are also treated as a part of the
-predicates when checking the satisfiability. Here we need conduct some
-translations, such as $\{s_0 \leftarrow 1\}$ in section
+predicates when checking the satisfiability. % Here we need conduct some
+% translations,
+For each assignement in a $\Post$ predicate, such as $\{s_0 \leftarrow 1\}$ in section
 ~\ref{section:op-semantics}, we translate it into an equation
-$s_0=1$. Then for the assignments of the same variable, we keep all
-possible equations, and generate the disjunction of
+$s_0=1$. For several assignments of the same variable in the same state,
+we generate the disjunction of 
 these equations. Correspondingly, we generate a conjunction for the
-assignments from the different variables.
+assignments from different variables.
 
@@
 
-\QIN{[The fig is improved. A little change on the comments.]}
+% \QIN{[The fig is improved. A little change on the comments.]}
 
@@
 
-\QIN{
-yields 30 open
+Our tool builds 30 open
 transitions, out of which 27 are detected unsatisfiable by Z3, we
@@
 Fig. ~\ref{schema:lotos-result}, together with its open transitions.
-}
 

### 2017-06-21 2017-Xudong-SMT/submit-ICTAC2017.tex
Remove the CCS example. Restructure the S5.
Sketch to the head.
Section 5.1 -> Section 5.3.

@@
 Section \ref{section:op-semantics} recalls the operational semantics
-of pNet, including its structural rules, and a sketch of the algorithm
-to compute such semantics, but also explains the enhancement we have
-done to these definitions.
+of pNet, including its structural rules
+%, and a sketch of the algorithm
+%to compute such semantics, but also explains the enhancement we have
+%done to these definitions
+.
 Section \ref{section:implementation} explains in details our
@@
 
-Each state has its set of variables called state variables.
-$State\ variables$ can only be modified by the assignment in the transitions targeting its owner state. 
+Each state has its set of variables called $State\ variables$, 
+which can only be modified by the assignment in the transitions targeting its owner state. 
 A global state variable of a pLTS is a variable $x$ satisfying $\forall s\!\in\! S .\, x\!\in\! \vars(s)$.
@@
 \TODO{I'm thinking about moving this second example to section 5...}
-
-\subsection{CCS Parallel Example}
-
-\begin{figure}[h]
-  \centerline{\includegraphics[width=10cm]{XFIG/CCS1.eps}}
-  \caption{pNet encodings for the CCS expression}  \label{schema:ccs-pnet}
-\end{figure}
-
-\QIN{
-This CCS expression composing two operators, parallel and prefix. In Fig.~\ref{schema:ccs-pnet}, 
-it is easy to recognize that the pNets $PN2$ and $PN3$ are similar to 
-the sub-pNet in the LOTOS example in their structure and synchronization vectors. 
-That is because they are the operators conduct a similar behavior from different algebras.
-}
-
-\QIN{
-To present the parallel property, we have defined a set of synchronization vectors composing 
-two subnets. We use the notation from the CCS to present the emit and receive action. 
-The variables $v_1$, $v_2$ are the data transmitting between two components, 
-showing its value-passing behavior.
-}
+\QIN{[This CCS example is removed.]}
+
+%\subsection{CCS Parallel Example}
+%
+%\begin{figure}[h]
+%  \centerline{\includegraphics[width=10cm]{XFIG/CCS1.eps}}
+%  \caption{pNet encodings for the CCS expression}  \label{schema:ccs-pnet}
+%\end{figure}
+%
+%\QIN{
+%This CCS expression composing two operators, parallel and prefix. In Fig.~\ref{schema:ccs-pnet}, 
+%it is easy to recognize that the pNets $PN2$ and $PN3$ are similar to 
+%the sub-pNet in the LOTOS example in their structure and synchronization vectors. 
+%That is because they are the operators conduct a similar behavior from different algebras.
+%}
+%
+%\QIN{
+%To present the parallel property, we have defined a set of synchronization vectors composing 
+%two subnets. We use the notation from the CCS to present the emit and receive action. 
+%The variables $v_1$, $v_2$ are the data transmitting between two components, 
+%showing its value-passing behavior.
+%}
 
@@
 
+\QIN{
+For the open pNets, in previous work, we already have a sketch for computing the open automaton.
+}
+
+\QIN{
+1) Start with the initial state of the automaton. 
+}
+
+\QIN{
+2) Apply Tr1 and Tr2 to deduct all the possible open transitions. Use SMT solver to prune the 
+unsatisfiable transitions. Recursively conduct this step with the target state of the transitions 
+until all the global states are explored.
+}
+
+\QIN{
+3) Finally a reachability check could potentially prune the state space.
+}
+
+However, more details are needed when doing the implementation. 
 In our prototype we start directly with open pNets expressed
 programmatically, using the pNet API (graphical editors may be added
-later). From these, we compute
-the open automaton of an open pNet. We explain here our main
-implementation choices.
+later). 
+%From these, we compute
+%the open automaton of an open pNet. We explain here our main
+%implementation choices.
 %:
@@
 
-\subsection{Fresh variables}
-
-%The variables in each synchronization vector are considered local, so
-%does the variables of an open transition such as its hole behaviors
-%and its result action. So we want rename the variables to make them
-%unique on every occurrence of a vector. Similarly, the name given to
-%the hole behaviors for each hole or the result action for each open
-%transition must be distinct. At the same time, we also hope them still
-%readable. Here we rename the variables with a regular format using the fresh function.
-
-Application of the semantic rules require generating a lot of fresh
-names, for different kind of variables. We could use a global name
-generator to guarantee unicity, but 
-at the same time, we also hope them still
-readable. Here we rename the variables with a regular format using the fresh function.
-More precisely, the fresh function generates a new name adding a
-suffix after the original name. The suffix contains three parts
-combined by a colon.
-
-\begin{definition}[Fresh variable]\label{fresh-variable}
-The format of \emph{fresh variable} (renaming) is defined as:
-``$\emph{prefix : tree\ index\ :\ counter}$''.
-\begin{itemize}
-   \item[$\bullet$] $prefix$ identifies the kind of the
-     variable. current kinds are: sva (SV action), ra (result action), hb (hole behavior).
-   \item[$\bullet$] $tree\ index$ is the index of the node containing the variable in the tree-like structure of the pNet.
-   \item[$\bullet$] $counter$ is the current value of the corresponding counter.
-\end{itemize}
-\end{definition}
-
-%\TODO{Option: Add the process and the vector ids ?}
-
-%$Prefix$ avoids the confusion between variables from different structures with the same name by attaching the type of the structure.
-$Tree\ index$ is given to every node of the pNets to mention which node the variable belongs to as pNets has a tree-like structure.
-To each node, the tree index is always a number sequence of the tree index of its higher level and the index of the node in this level at the last.
-$A\ set\ of\ counters$ is used to count the current times the SV, Hole, subnet invoked, or the number of possible OT generated to provide an identity.
-
-For example, in the running example, the first possible behavior of
-the hole, it doesn't have a name, only have the prefix ``hb''. The
-hole is the second subnets of the root node so its ``tree index'' is
-``12''. The fresh variable name is ``$\OTvar{:hb:12:1}$''.
-
 %\TODO{I have not yet been in details through the next section, but we
@@
 \TODO{Xudong: move here a (new version) of the alogorithm loplevel sketch}
-\QIN{
-In previous work, we already have a sketch for computing the open automaton.
-}
-
-\QIN{
-1) Start with the initial state of the automaton. 
-}
-
-\QIN{
-2) Apply Tr1 and Tr2 to deduct all the possible open transitions. Use SMT solver to prune the 
-unsatisfiable transitions. Recursively conduct this step with the target state of the transitions 
-until all the global states are explored.
-}
-
-\QIN{
-3) Finally a reachability check could potentially prune the state space.
-}
+\QIN{[Move to the head of Section 5.]}
 
@@
 The detail about the application of the Tr1 and Tr2 have not considered in the sketch, but it is an  
-important part in the implementation of open transition generation. Each time we apply Tr1, there is not too much predicate terms, so do the other parameters, needed 
-to be generated. When it comes to applying Tr2, the computation becomes complicated because it doing some composition of the subnets.
+important part in the implementation of open transition generation. 
+Each time we apply Tr1, there is not too much predicate terms, so do the other parameters, needed 
+to be generated. 
+When it comes to applying Tr2, the computation becomes complicated because it doing some composition of the subnets.
 }
@@
 
+\subsection{Fresh variables}
+
+%The variables in each synchronization vector are considered local, so
+%does the variables of an open transition such as its hole behaviors
+%and its result action. So we want rename the variables to make them
+%unique on every occurrence of a vector. Similarly, the name given to
+%the hole behaviors for each hole or the result action for each open
+%transition must be distinct. At the same time, we also hope them still
+%readable. Here we rename the variables with a regular format using the fresh function.
+
+Application of the semantic rules require generating a lot of fresh
+names, for different kind of variables. We could use a global name
+generator to guarantee unicity, but 
+at the same time, we also hope them still
+readable. Here we rename the variables with a regular format using the fresh function.
+More precisely, the fresh function generates a new name adding a
+suffix after the original name. The suffix contains three parts
+combined by a colon.
+
+\begin{definition}[Fresh variable]\label{fresh-variable}
+The format of \emph{fresh variable} (renaming) is defined as:
+``$\emph{prefix : tree\ index\ :\ counter}$''.
+\begin{itemize}
+   \item[$\bullet$] $prefix$ identifies the kind of the
+     variable. current kinds are: sva (SV action), ra (result action), hb (hole behavior).
+   \item[$\bullet$] $tree\ index$ is the index of the node containing the variable in the tree-like structure of the pNet.
+   \item[$\bullet$] $counter$ is the current value of the corresponding counter.
+\end{itemize}
+\end{definition}
+
+%\TODO{Option: Add the process and the vector ids ?}
+
+%$Prefix$ avoids the confusion between variables from different structures with the same name by attaching the type of the structure.
+$Tree\ index$ is given to every node of the pNets to mention which node the variable belongs to as pNets has a tree-like structure.
+To each node, the tree index is always a number sequence of the tree index of its higher level and the index of the node in this level at the last.
+$A\ set\ of\ counters$ is used to count the current times the SV, Hole, subnet invoked, or the number of possible OT generated to provide an identity.
+
+For example, in the running example, the first possible behavior of
+the hole, it doesn't have a name, only have the prefix ``hb''. The
+hole is the second subnets of the root node so its ``tree index'' is
+``12''. The fresh variable name is ``$\OTvar{:hb:12:1}$''.
+
 \subsection{Management of state variable assignments}
@@
 $x$ is transmitted to the $acc(x);Q$ giving out a silent action. Such behavior is performed by the $ot_1$ and $ot_2$. 
-Then it keeps presenting the behavior of $Q$. $ot_3$ has showed that. 
+Then it keeps presenting the behavior of $Q$. This can also be seen in $ot_3$. 
 %The $ot_1$ transition means that the actions of the process $P$ could
@@
 
-\subsubsection{Result of CCS example}
-\QIN{
-also can present all the possible behavior of that CCS formula with 16 open
-transitions in Fig. ~\ref{schema:ccs-result}, here we omitted the details of open transitions. 
-In this example, there are 32 more transitions detected unsatisfiable by Z3.
-}
-
-\QIN{
-Here we only show one of the result transitions. It presents the value-passing between $a.P$ and $b.Q$ and they are synchronized then
-give out an silent action $\tau$, process $P$ and $Q$ should not work in this case.
-}
-
-\begin{figure}[h]
-  \centerline{\includegraphics[width=5cm]{XFIG/CCSresult}}
-
-  $\begin{array}{@{}r@{}l@{}}
-    ot_1  = &\openrule{\{0 \xrightarrow{a}_{C_1} 1, 0 \xrightarrow{b}_{C_2} 1\}, ~~a=!ch_{11}(v_{11}) \!\land\! b=?ch_{11}(v_{11}) \!\land\! a\neq l \!\land\! b\neq r\!\land\! v_1=\tau}
-    {\ostate{00} \xrightarrow{v_1} \ostate{11}}\\
-  \end{array}$
-
-\caption{The open automaton of the CCS parallel formula}  \label{schema:ccs-result}
-\end{figure}
+%\subsubsection{Result of CCS example}
+%\QIN{
+%also can present all the possible behavior of that CCS formula with 16 open
+%transitions in Fig. ~\ref{schema:ccs-result}, here we omitted the details of open transitions. 
+%In this example, there are 32 more transitions detected unsatisfiable by Z3.
+%}
+%
+%\QIN{
+%Here we only show one of the result transitions. It presents the value-passing between $a.P$ and $b.Q$ and they are synchronized then
+%give out an silent action $\tau$, process $P$ and $Q$ should not work in this case.
+%}
+%
+%\begin{figure}[h]
+%  \centerline{\includegraphics[width=5cm]{XFIG/CCSresult}}
+%  
+%  $\begin{array}{@{}r@{}l@{}}
+%    ot_1  = &\openrule{\{0 \xrightarrow{a}_{C_1} 1, 0 \xrightarrow{b}_{C_2} 1\}, ~~a=!ch_{11}(v_{11}) \!\land\! b=?ch_{11}(v_{11}) \!\land\! a\neq l \!\land\! b\neq r\!\land\! v_1=\tau}
+%    {\ostate{00} \xrightarrow{v_1} \ostate{11}}\\
+%  \end{array}$
+%  
+%\caption{The open automaton of the CCS parallel formula}  \label{schema:ccs-result}
+%\end{figure}
 

### 2017-06-21 2017-Xudong-SMT/submit-ICTAC2017.tex
claen sectino 3

@@
 Section \ref{section:op-semantics} recalls the operational semantics
-of pNet, including its structural rules
+of pNet, including its structural rules.
 %, and a sketch of the algorithm
@@
 %done to these definitions
-.
 Section \ref{section:implementation} explains in details our
@@
 
+ \begin{figure}[t]
+   \centerline{\includegraphics[width=10cm]{XFIG/LOTOSFormula.eps}}
+   \caption{pNet encodings for the LOTOS expression}  \label{schema:lotos-pnet}
+ \end{figure}
+
 In this paper, we use an example inspired from LOTOS, to illustrate
@@
 semantics, and in the satisfiability checking. 
-\QIN{
-Meanwhile, 
-the formula using operators from CCS can also be encoded into a pNet and 
-conducted with the same things.
-}
-
-\subsection{LOTOS Formula Example}
-
-\begin{figure}[h]
-  \centerline{\includegraphics[width=10cm]{XFIG/LOTOSFormula.eps}}
-  \caption{pNet encodings for the LOTOS expression}  \label{schema:lotos-pnet}
-\end{figure}
-
-We choose the expression \texttt{P>>(acc(v);Q)}, that includes the
+%% \QIN{
+%% Meanwhile, 
+%% the formula using operators from CCS can also be encoded into a pNet and 
+%% conducted with the same things.
+%% }
+%% \subsection{LOTOS Formula Example}
+We choose here the expression \texttt{P>>(acc(v);Q)}, that includes the
 Enable and Prefix 
@@
 
-\TODO{I'm thinking about moving this second example to section 5...}
-\QIN{[This CCS example is removed.]}
+%% \TODO{I'm thinking about moving this second example to section 5...}
+%% \QIN{[This CCS example is removed.]}
 
@@
 
-\TODO{ERIC: after we move / replace Algoriithm 1, this will not make sense any longer. I will replace it with a more informal paragraph, in section 5}
+%% \TODO{ERIC: after we move / replace Algoriithm 1, this will not make sense any longer. I will replace it with a more informal paragraph, in section 5}
 

### 2017-06-21 2017-Xudong-SMT/submit-ICTAC2017.tex
Add the top-level algorithm.

@@
 However, more details are needed when doing the implementation. 
+Algorithm 1 shows there are much more things added, such as how we apply 
+the Tr1 or Tr2.
+
+\begin{algorithm}
+\caption{Open Automaton Generation}
+\begin{algorithmic}[1]
+
+\State Initialize a set for unexplored global states $U$, a set for explored global states $E$;
+\State Initialize the initial global state $G$ of the open automaton, add it into $U$;
+\State Initialize a list $L$ for storing open transitions;
+\While{!isEmpty(U)}
+	\State Extract a global state $S$ from the $U$;
+	\State For the pNet node, recursively applying Tr1 or Tr2 on its subnets;
+	\If{Subnet is pLTS, apply the Tr1} 
+		\State Generate open transition $OT$ according to the transitions in pLTS;
+	\EndIf
+	\If{Subnet is pNet, apply the Tr2} 
+		\For{each $sv \in SV$}
+			\State Invoke $Combining()$ to generate the combination of sub-transitions;
+			\State Invoke $Matching()$ to match the combination with the $sv$;
+			\State Generate open transition $OT$ using the predicate from the former steps;
+		\EndFor
+	\EndIf
+	\State Store $OT$ into $L$;
+	\State Get the target global state $T$ from $OT$;
+	\If{$(U.contains(T))\ ||\ (E.contains(T))$} 
+		\State Add $T$ into the $U$;
+	\EndIf
+\EndWhile
+\State Prune the open transitions in $L$ using SMT solver;
+\State \Return $L$;
+
+\end{algorithmic}  
+\end{algorithm}
+
 In our prototype we start directly with open pNets expressed
@@
 \paragraph{Combining:}
-Algorithm 1 shows the combining algorithm for enumerating all possible
+Algorithm 2 shows the combining algorithm for enumerating all possible
 working status combinations from subnets. Dealing with a list $TR$
@@
 
-\paragraph{Matching:} Algorithm 2 shows the algorithm matches
+\paragraph{Matching:} Algorithm 3 shows the algorithm matches
 combination $L_C$, hole behaviors $B$ with synchronization vectors

### 2017-06-21 2017-Xudong-SMT/submit-ICTAC2017.tex
head of s5

@@
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
+\algnewcommand{\IfThen}[2]{\State \algorithmicif\ #1\ \algorithmicthen\ #2}% \IfThenElse{<if>}{<then>}
 \algnewcommand{\IfThenElse}[3]{\State \algorithmicif\ #1\ \algorithmicthen\ #2\ \algorithmicelse\ #3}% \IfThenElse{<if>}{<then>}{<else>}
@@
 % variables.
-Action terms for pNets are defined as follows:
-\[\begin{array}[l]{rcl@{\quad}l}
-  \alpha\in \AlgAS &::=&a(Expr_1,\ldots,Expr_n)
-\end{array}
-\]
+%Action terms for pNets are defined as follows:
+%\[\begin{array}[l]{rcl@{\quad}l}
+%  \alpha\in \AlgAS &::=&a(Expr_1,\ldots,Expr_n)
+%\end{array}
+%\]
 
@@
 
-\begin{example}\emph{An open-transition.}
-  \label{OT:lotos-composed}
-
-The \texttt{LOTOS} pNet of Fig. \ref{schema:lotos-pnet} has 2
-controllers and 2 holes. We will show its full open Automaton in
-section \ref{section:full-result}. We give one of its transitions here:
-
- \smallskip
- $ ot_2  = \openrule{
-                       \{0 \xrightarrow{\delta}_{C_1} 0, 0 \xrightarrow{acc(x)}_{C_2} 1\}, ~~
-                       \{\xrightarrow{hb_{12}}_P\}, ~~ 
-                        [s_0=0 \!\land\! hb_{12}=\delta(x)], ~~ 
-                       \{s_0 \xleftarrow{} 1\}     
-                      }
-     {\ostate{00} \xrightarrow{\underline{\delta(x)}} \ostate{01}}$
-\end{example}
-
-The open transition $ot_2$ involves the possible actions from the process $P$ and prefix expression $acc(x);Q$.
+%\begin{example}\emph{An open-transition.}
+%  \label{OT:lotos-composed}
+%
+%The \texttt{LOTOS} pNet of Fig. \ref{schema:lotos-pnet} has 2
+%controllers and 2 holes. We will show its full open Automaton in
+%section \ref{section:full-result}. We give one of its transitions here:
+%
+% \smallskip
+% $ ot_2  = \openrule{
+%                       \{0 \xrightarrow{\delta}_{C_1} 0, 0 \xrightarrow{acc(x)}_{C_2} 1\}, ~~
+%                       \{\xrightarrow{hb_{12}}_P\}, ~~ 
+%                        [s_0=0 \!\land\! hb_{12}=\delta(x)], ~~ 
+%                       \{s_0 \xleftarrow{} 1\}     
+%                      }
+%     {\ostate{00} \xrightarrow{\underline{\delta(x)}} \ostate{01}}$
+%\end{example}
+%
+%The open transition $ot_2$ involves the possible actions from the process $P$ and prefix expression $acc(x);Q$.
 The hole behavior, represented by variable $hb_{12}$ must be equal to the exit action $\delta(x)$, and the accept event $acc(x)$ will capture the same value $x$.
-
-The transition in the conclusion of this rule starts in
-state $\ostate{00}$, where both $C_1$ and $C_2$ are in their initial
-states. It ends in a different structured state, because in $ot_2$
-both pLTS conduct transitions, showing that the control has gone from
-processes $P$ to $(acc(x);Q$, consuming actions $\delta(x)$ and
-$acc(x)$. Controller $C_1$ has only one state, but its state variable
-$s_0$ has changed to 1.
+%
+%The transition in the conclusion of this rule starts in
+%state $\ostate{00}$, where both $C_1$ and $C_2$ are in their initial
+%states. It ends in a different structured state, because in $ot_2$
+%both pLTS conduct transitions, showing that the control has gone from
+%processes $P$ to $(acc(x);Q$, consuming actions $\delta(x)$ and
+%$acc(x)$. Controller $C_1$ has only one state, but its state variable
+%$s_0$ has changed to 1.
 
@@
 
-\QIN{
-For the open pNets, in previous work, we already have a sketch for computing the open automaton.
-}
-
-\QIN{
-1) Start with the initial state of the automaton. 
-}
-
-\QIN{
-2) Apply Tr1 and Tr2 to deduct all the possible open transitions. Use SMT solver to prune the 
-unsatisfiable transitions. Recursively conduct this step with the target state of the transitions 
-until all the global states are explored.
-}
-
-\QIN{
-3) Finally a reachability check could potentially prune the state space.
-}
-
-However, more details are needed when doing the implementation. 
-Algorithm 1 shows there are much more things added, such as how we apply 
-the Tr1 or Tr2.
-
 \begin{algorithm}
@@
 \State Initialize a set for unexplored global states $U$, a set for explored global states $E$;
-\State Initialize the initial global state $G$ of the open automaton, add it into $U$;
-\State Initialize a list $L$ for storing open transitions;
 \While{!isEmpty(U)}
 	\State Extract a global state $S$ from the $U$;
-	\State For the pNet node, recursively applying Tr1 or Tr2 on its subnets;
+	\State Start at the root pNet node
+	\State Recursively applying Tr1 or Tr2 on it and its subnets;
 	\If{Subnet is pLTS, apply the Tr1} 
-		\State Generate open transition $OT$ according to the transitions in pLTS;
+		\For{each transition $TR$ start from the state $s$ in $S$}
+			\State Generate open transition $OT$ according to $TR$;
+			\State Store $OT$ into the result list $L$;
+		\EndFor
 	\EndIf
@@
 			\State Invoke $Matching()$ to match the combination with the $sv$;
-			\State Generate open transition $OT$ using the predicate from the former steps;
+			\State Store the result set of open transitions into $L$;
 		\EndFor
 	\EndIf
-	\State Store $OT$ into $L$;
-	\State Get the target global state $T$ from $OT$;
-	\If{$(U.contains(T))\ ||\ (E.contains(T))$} 
-		\State Add $T$ into the $U$;
-	\EndIf
+	\For{each target global state $T$ from $OT \in L$}
+		\IfThen{$(!U.contains(T))\ \&\&\ (!E.contains(T))$}{Add $T$ into the $U$;}
+	\EndFor
 \EndWhile
@@
 \end{algorithm}
+
+\QIN{
+For the open pNets, in previous work, we already have a sketch for computing the open automaton.
+The computation repeats applying Tr1 and Tr2 to deduct all the possible open transitions and pruning the 
+unsatisfiable transitions by SMT solver until all the global states are explored. 
+In the end, a reachability check is supposed to potentially prune the state space. 
+Algorithm 1 is what we used in the implementation, there are much more details added based on 
+the sketch, such as how we apply the Tr1 or Tr2.
+}
 

### 2017-06-21 2017-Xudong-SMT/submit-ICTAC2017.tex
done pages 5 and 8

@@
 \begin{definition}[pNets]\label{def-pnets}
-A pNet is a hierarchical structure where leaves are pLTSs and holes:\\
+A pNet is a hierarchical structure which leaves are pLTSs and holes:\\
 $\pNet\triangleq pLTS~|~\mylangle \pNet_i^{i\in I}, S_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle$
@@
 $I$ and $J$ are \emph{disjoint}: $I\cap J=\emptyset$,  $I\cup J\neq\emptyset$
-\item[$\bullet$] $S_j \subseteq \AlgAS$ is a set of action terms, denoting the $\Sort$ of
-hole $j$.
+
+\item[$\bullet$] $S_j \subseteq \AlgA$ is a set of action terms,
+  denoting the $\Sort$\footnote{The formal definition of $Sorts$ (set of actions of a Hole
+  or pNet), $Leaves$ and $Holes$ (all pLTSs (resp holes) in a pNet
+  hierarchical system. These can be found in \cite{henrio:Forte2016}.}
+  of hole $j$.
 
@@
   $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
-  $\forall i\!\in\!
-  I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$,  $\forall j\!\in\!
+  $\forall i\!\in\! I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$,
+  $\forall j\!\in\!
   J_k.\,\alpha_{j}\!\in\!S_j$, and $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
@@
 
-By lack of space, we have omitted here the formal (structural)
-definition of $Sorts$ (the 
-set of actions of a hole or a pNet), $Leaves$ and $Holes$ (all pLTSs
-(resp holes) in a pNet hierarchical system. These can be found in \cite{henrio:Forte2016}.
 %The preceding definition relies on the auxiliary functions below:
@@
 fresh one.
+The variables in each synchronization vector are considered local:
+for a given pNet expression, we must have fresh local variables for
+each occurrence of a vector (= each time we instantiate rule
+Tr2). Similarly the state variables of each copy of a
+given pLTS in the system, must be distinct, and those created for each
+application of Tr2 have to be fresh and all distinct.
 
@@
 
-\paragraph{Fresh variables management.}
-The variables in each synchronization vector are considered local:
-for a given pNet expression, we must have fresh local variables for
-each occurrence of a vector (= each time we instantiate rule
-Tr2). Similarly the state variables of each copy of a
-given pLTS in the system, must be distinct, and those created for each
-application of Tr2 have to be fresh and all distinct. 
+%\paragraph{Fresh variables management.}
+
 % This will be implemented within the open-automaton generation algorithm,

### 2017-06-21 2017-Xudong-SMT/submit-ICTAC2017.tex
reduce section 2

@@
 \begin{itemize}
-  \item To get a tool that could be applied to pNets representing
+  \item to get a tool that could be applied to pNets representing
     various languages, in particular various actions algebras,
-    with their specific decision theories.
-  \item To separate clearly the algorithmic part, as a residual
+    with their specific decision theories,
+  \item to separate clearly on one hand the algorithmic part, as an
       algorithm generating the transitions of the open automaton from
-      combination of all possible (symbolic) behaviors on one hand; from the
-      symbolic reasonning part, specificaly here checking the
+      combination of all possible (symbolic) behaviors; on the other hand
+      the symbolic reasonning part, specificaly here using an SMT
+      engine to check the
       satisfiability of the predicates generated by our algorithm,
-      that we delegate to a generic SMT engine, on the other hand.
-  \item To build a prototype and validate the approach on our basic
+  \item to build a prototype and validate the approach on our basic
     case-studies, and understand the efficiency of the interaction
@@
 \begin{itemize}
-\item We have defined the open automaton generation algorithm, and we
+\item We define the open automaton generation algorithm, and we
   implemented a full working prototype, within the 
-  VerCors platform. In the process, we had to improve significantly the
+  VerCors platform. In the process, we improved the
   semantics rules from~\cite{henrio:Forte2016}, and add features in
@@
 %    parameterisation over the action algebra operators.
-\item We have implemented the interaction between our algorithm and the Z3
-    SMT solver, for checking satisfiability of the logical predicates
+\item We implement the interaction between our algorithm and the Z3
+    SMT solver, for checking satisfiability of the transitions
     generated by the algorithm.
-\item We validated the whole approach on small use-cases covering all
+\item We validate the whole approach on small use-cases covering all
       important features of the model.
@@
 This pNet is composed of: a toplevel node PN1 encoding the Enable
-operator, with its controller (pLTS) C1; a hole representing the
+operator, a pLTS C1 acting as the {\sl controller} of the node; a hole
+representing the 
 process variable P; another node PN2 representing the Prefix
@@
 styles of encodings in the controllers.
-The most common style used in process calculi is ``state oriented'',
-we use it here for C2: it has two states to
+% The most common style used in process calculi is ``state oriented'',
+Controller C2 is ``state oriented'': it has two states to
 indicate the position of the control point in the
@@
 
-Now consider the top pNet node PN1. In addition to
-its controller it has 2 sub-pNets: the hole P and the sub-pNet PN2.
+The root pNet node PN1 has 3 sub-pNets: its controller C1,
+the hole P and the sub-pNet PN2.
 Three synchronization vectors define the possible
-synchronizations between the actions of its subnets.
-The first vector ``$< l, a_1 , \_ > -> a_1$'', transmitting an action
-$a_1$ of P, can only occur if $a_1$ is not  
-a $\delta$, here ``$\_$'' means that the corresponding subnet is
-not involved in this synchronization, and the ``l'' action is related
-to the corresponding transition of the controller C1: this action is
-available only when the state variable $s_0$ is equal to 0.
+synchronizations between the actions of the subnets.
+The first vector ``$< l, a_1 , \_ > -> a_1$'' transmits an action
+$a_1$ of P to the upper level. Here the ``l'' action is related
+to the corresponding transition of the controller C1, ``$\_$'' means
+that the corresponding subnet is not involved in this synchronization,
+and there is a guard meaning this synchronisation can only occur if
+$a_1$ is not a $\delta$.
 The second synchronisation vector composes an
@@
 value $x$ before $Q$ takes the control; 
-The vector result $\underline{\delta(x)}$ is an
-internal action, called ``synchronized'' that cannot be further
-synchronized at upper levels. Synchronized actions is a straightforward
+The vector result $\underline{\delta(x)}$ is a ``synchronized''
+action, that cannot be further
+synchronized at upper levels. Synchronized actions is a useful
 generalization of the notion of internal actions, that will be
 convenient for observing internal events during model-checking.
-The last vector acts is to the first one.  
-Similarly the node PN2 has two synchronization vectors to encode
-the behavior of the Prefix operator.
+% The last vector acts is to the first one.  
+% Similarly the node PN2 has two synchronization vectors to encode
+% the behavior of the Prefix operator.
 
@@
 
-This definition is not constructive but it is easy to build the
-predicate constructively by brute-force unification of the sub-pNets
-actions with the corresponding vector actions, possibly followed by a simplification
-step.
+%% This definition is not constructive but it is easy to build the
+%% predicate constructively by brute-force unification of the sub-pNets
+%% actions with the corresponding vector actions, possibly followed by a simplification
+%% step.
 
@@
 LTSs are the pLTSs at 
-the leaves of the pNet structure, and the states are structured as in
+the pNet leaves, and the states are structured as in
 the previous section. 
 %given by Definition~\ref{def-states}.
-The open transitions first
- project the global state into states of the leaves, then apply
-pLTS transitions on these states, and compose them with the sort of the holes. %The pNet
+To build an open transition one first
+ projects the global state into states of the leaves, then applies
+pLTS transitions on these states, and compose them with actions of
+holes using synchronisation vectors. %The pNet
 %structure does not appear in the open-automaton, only the
 %set of Holes and the set of Leaves.
+
 The semantics   regularly instantiates \emph{fresh} variables, and uses a
@@
 
-  The rule for a pLTS $p$  checks that the guard 
+  The rule ({\bf Tr1}) for a pLTS $p$  checks that the guard 
   is verified and transforms assignments into post-conditions:
@@
       {\tt fresh}(v) \\
-      Pred = ~e_b \land (\alpha = v)
+      Pred = ~e_b \land (v = \alpha)
     }
@@
 
-\State Initialize a set for unexplored global states $U$, a set for explored global states $E$;
+\State Initialize sets $U$, $E$ for unexplored/explores global states
+$U$, $L$ for result OTs;
 \While{!isEmpty(U)}
 	\State Extract a global state $S$ from the $U$;
-	\State Start at the root pNet node
-	\State Recursively applying Tr1 or Tr2 on it and its subnets;
-	\If{Subnet is pLTS, apply the Tr1} 
-		\For{each transition $TR$ start from the state $s$ in $S$}
-			\State Generate open transition $OT$ according to $TR$;
-			\State Store $OT$ into the result list $L$;
+	\State Recursively applying Tr1 or Tr2 on the root node and its subnets:
+	\If{Subnet is pLTS}
+                \State $s$ is the local state of the pLTS in the global state $S$;
+		\For{each transition $tr$ starting from $s$}
+			\State apply Tr1 to build the corresponding
+                        $OT$; store $OT$ in $L$;
 		\EndFor
@@
 \subsection{Combining and Matching using TR2}
-\TODO{Xudong: move here a (new version) of the alogorithm loplevel sketch}
-\QIN{[Move to the head of Section 5.]}
+% \TODO{Xudong: move here a (new version) of the alogorithm loplevel sketch}
+% \QIN{[Move to the head of Section 5.]}
 

### 2017-06-21 2017-Xudong-SMT/submit-ICTAC2017.tex
16 pages versin - submitted

@@
 
-In this paper, we use an example inspired from LOTOS, to illustrate
-the main features of pNets and the way we deal with them in the symbolic
-semantics, and in the satisfiability checking. 
+We use an example inspired from LOTOS, to illustrate
+the main features of pNets and our semantic construction algorithm.
 %% \QIN{
@@
 When building an Open Automaton as the semantics of a pNet, its
-\emph{states}, and the shape of the predicates in its
-\emph{transitions} have a specific structure:
+\emph{states}, and the shape of the \emph{predicates} in its
+transitions have a specific structure:
 
 \paragraph{States of open pNets:}\label{def-states}
-  A state of an open pNet is a tuple (not necessarily finite) of the
+  A state of an open pNet is a tuple of the
   states of its leaves (in which we denote tuples
-  in structured states as $\triangleleft\ldots\triangleright$ for better readability).
-
+  in structured states as $\triangleleft\ldots\triangleright$).
   For any pNet p, let $\overline{Leaves} = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be the set of pLTS at its leaves,
@@
   $States(\mylangle S,s_0, \to\myrangle) = \{\triangleleft s \triangleright| s \in S\}$.
-
 The initial state is defined as:
@@
 \end{array}\]
-In any other case (if the action families do not match or if there is no valuation of
-variables such that the above formula can be ensured) the predicate is undefined.
+%% In any other case (if the action families do not match or if there is no valuation of
+%% variables such that the above formula can be ensured) the predicate is undefined.
 
@@
 \begin{figure}[h]
-  \vspace{-10mm}
+%  \vspace{-10mm}
 
@@
 \label{section:implementation}
-The VerCors platform uses (closed) pNets as the intermediate language
+The VerCors platform uses pNets as the intermediate language
 for some high-level language or graphical formalism to be translated
-into both input for a 
-model-checker and for generating executable code automatically \cite{HKM-FASE16}.
-% to ease the
-% specification from non-expert users, compiling it
-%from those language or graphical formalism in the pNet API.
+into both input for a model-checker and for generating executable code
+automatically \cite{HKM-FASE16}.
+We have extended the pNet API in VerCors to deal with open pNets, and
+also to specify the structure of action algebras.
+
+In this section we describe the algorithm implementing the pNet
+semantics, the interaction with the Z3 SMT solver, and we show the
+result on our  example.
 
@@
 
-\State Initialize sets $U$, $E$ for unexplored/explores global states
+\State Initialize sets $U$, $E$ for unexplored/explored global states
 $U$, $L$ for result OTs;
 \While{!isEmpty(U)}
-	\State Extract a global state $S$ from the $U$;
-	\State Recursively applying Tr1 or Tr2 on the root node and its subnets:
-	\If{Subnet is pLTS}
+	\State Chose a global state $S$ in $U$; recursively applying Tr1 or Tr2 on the root node;
+	\If{Subnet is a pLTS}
                 \State $s$ is the local state of the pLTS in the global state $S$;
@@
 			\State apply Tr1 to build the corresponding
-                        $OT$; store $OT$ in $L$;
-		\EndFor
+                        $OT$; store $OT$ in $L$; \EndFor
 	\EndIf
-	\If{Subnet is pNet, apply the Tr2} 
+	\If{Subnet is a pNet, apply Tr2:} 
 		\For{each $sv \in SV$}
-			\State Invoke $Combining()$ to generate the combination of sub-transitions;
-			\State Invoke $Matching()$ to match the combination with the $sv$;
-			\State Store the result set of open transitions into $L$;
+			\State Invoke $Combining()$ to generate the
+                        combination of sub-transitions, $Matching()$
+                        to match the combination with the $sv$; then
+                        store the result OTs in    $L$; 
 		\EndFor
@@
 \EndWhile
-\State Prune the open transitions in $L$ using SMT solver;
+\State Prune the open transitions in $L$ using the SMT solver;
 \State \Return $L$;
@@
 
-\QIN{
-For the open pNets, in previous work, we already have a sketch for computing the open automaton.
-The computation repeats applying Tr1 and Tr2 to deduct all the possible open transitions and pruning the 
-unsatisfiable transitions by SMT solver until all the global states are explored. 
-In the end, a reachability check is supposed to potentially prune the state space. 
-Algorithm 1 is what we used in the implementation, there are much more details added based on 
-the sketch, such as how we apply the Tr1 or Tr2.
-}
-
-In our prototype we start directly with open pNets expressed
-programmatically, using the pNet API (graphical editors may be added
-later). 
+Algorithm 1 shows the main structure of the algorithm: 
+the computation repeats applying Tr1 and Tr2 to build all possible
+combinations of behaviors of pLTS and Holes, through all possible
+synchronisation vectors. The resulting open transitions are checked
+for satisfiability by the SMT solver.
+
 %From these, we compute
@@
 
-\subsection{Combining and Matching using TR2}
 % \TODO{Xudong: move here a (new version) of the alogorithm loplevel sketch}
@@
 
-\QIN{
-The detail about the application of the Tr1 and Tr2 have not considered in the sketch, but it is an  
-important part in the implementation of open transition generation. 
-Each time we apply Tr1, there is not too much predicate terms, so do the other parameters, needed 
-to be generated. 
-When it comes to applying Tr2, the computation becomes complicated because it doing some composition of the subnets.
-}
-
+%% \QIN{
+%% The detail about the application of the Tr1 and Tr2 have not considered in the sketch, but it is an  
+%% important part in the implementation of open transition generation. 
+%% Each time we apply Tr1, there is not too much predicate terms, so do the other parameters, needed 
+%% to be generated. 
+%% When it comes to applying Tr2, the computation becomes complicated because it doing some composition of the subnets.
+%% }
+
+%\paragraph{Combining and Matching using TR2}
 Our implementation does not build explicitly the proof trees for each
@@
 We get much more combinations after combining $ot$ from $L_{ot}$ with the partial result.
-
-\paragraph{Combining:}
-Algorithm 2 shows the combining algorithm for enumerating all possible
-working status combinations from subnets. Dealing with a list $TR$
-containing  sets of open transitions from different subnets,
-the algorithm choses one of sets $L_{ot}$ and does combining on the
-remaining part of $TR$ recursively. The case when a subnet is not working is
-managed by adding a $null$ into the $L_{ot}$.
 
@@
 \end{algorithm}
+
+\paragraph{Combining:}
+Algorithm 2 shows the combining algorithm for enumerating all possible
+working status combinations from subnets. Dealing with a list $TR$
+containing  sets of open transitions from different subnets,
+the algorithm choses one of sets $L_{ot}$ and does combining on the
+remaining part of $TR$ recursively. The case when a subnet is not working is
+managed by adding a $null$ into the $L_{ot}$.
 
@@
 %out.
-
-\paragraph{Matching:} Algorithm 3 shows the algorithm matches
-combination $L_C$, hole behaviors $B$ with synchronization vectors
-$SV$ according to the definition of the predicate declared before. We
-clone the $sv$ using the fresh function to generate a new $sv'$ with
-fresh variables.The mismatch on working status is easy to detect so we
-filter them in the algorithm through checking the matching elements
-$e_1$ and $e_2$. 
-Then we build the resulting open transition. Satisfiability of the
-predicate is not checked at this level, but only later, at the
-toplevel of the pNet.
 
@@
 
+\paragraph{Matching:} Algorithm 3 shows the algorithm matches
+combination $L_C$, hole behaviors $B$ with synchronization vectors
+$SV$ according to the definition of the predicate declared before. We
+clone the $sv$ using the fresh function to generate a new $sv'$ with
+fresh variables.The mismatch on working status is easy to detect so we
+filter them in the algorithm through checking the matching elements
+$e_1$ and $e_2$. 
+Then we build the resulting open transition. Satisfiability of the
+predicate is not checked at this level, but only later, at the
+toplevel of the pNet.
+
 \subsection{Fresh variables}
@@
 
-\subsubsection{Result of LOTOS example}
+% \subsubsection{Result of LOTOS example}
 
@@
 
-\QIN{
-The final result open transitions represent all the
+The resulting open transitions represent all the
 possible movements of the LOTOS example.
-What can be observed is always the actions of the process $P$ from the beginning, until $P$ performs a $\delta(x)$ and the value of
-$x$ is transmitted to the $acc(x);Q$ giving out a silent action. Such behavior is performed by the $ot_1$ and $ot_2$. 
-Then it keeps presenting the behavior of $Q$. This can also be seen in $ot_3$. 
+What can be observed is any actions of the process $P$ from the beginning, until $P$ performs a $\delta(x)$ and the value of
+$x$ is transmitted to the $acc(x);Q$ giving out a silent action. Such behavior is performed by the $ot_1$ then $ot_2$. 
+Then it keeps presenting the behavior of $Q$, as seen in $ot_3$. 
 %The $ot_1$ transition means that the actions of the process $P$ could
@@
 %action.
-}
 
@@
 
-\QIN{
-To sum up, from the pNets encoding the formulas of given algebra, which inputed by the user, we can exactly construct
-the open automaton for them. 
-}
+%% \QIN{
+%% To sum up, from the pNets encoding the formulas of given algebra, which inputed by the user, we can exactly construct
+%% the open automaton for them. 
+%% }
 
@@
 instantiations. 
-To get rid of these useless transitions, we use a SMT solver Z3 for checking the
+To get rid of these useless transitions, we use the SMT solver Z3 for checking the
 satisfiability of the predicate in each open transition. In
-order to do that, we have done some translation on the presentation,
-the predicate and the assignments of the variables which are also
-considered as a part of predicates before submitting them to the
+order to do that, we encode into Z3 the action algebra presentation,
+the a representation of the predicates, before submitting them to the
 Z3 solver. We implemented our algorithm in the VerCors platform and use some
-running examples, the formula from other process algebras, to test the
-algorithm. The result of the running examples are shown as the open
-automaton with all the parameters generated by the algorithm
-automatically. The open automaton successfully presents all the
-possible movements of the LOTOS expression.
+running examples, encoding expressions from various process algebras, to test the
+algorithm. Our use-cases show that our encoding
+identifies successfully all unsatisfiable open transitions and that
+the resulting automaton reflects correctly the expected 
+movements of the encoded process expressions.
 
@@
 
-Naturally, the next work after the generation of the open automata
-will be to check the bisimulation of the pNets. In previous paper, we
+Naturally, our next goals after the generation of the open automata
+will be to model-check, and to check equivalence of  pNets. While
+model-checking open automata (with a suitable logic including
+predicates on data) seems easy to define, equivalence checking is more challenging.
+In previous paper, we
 have already found the FH-bisimulation, inspired by~\cite{deSimone85} as a
-suitable definition. Usual approaches of bisimulation by partition
+suitable definition. But usual approaches of bisimulation by partition
 refinement does not work easily with symbolic transitions. In a first
-step we may want instead to define and implement an algorithm fo
-r checking that a given equivalence relation between open automata
+step we may want instead to define and implement an algorithm for
+checking that a given equivalence relation between open automata 
 states is indeed a FH-Bisimulation. Finding automatically a
@@
 Fig.~\ref{schema:lotos-result} is not the one generated by the algorithm,
-because it contains many intermediate
+because the original one contains many intermediate
 variables, such as fresh local variables of synchronization

### 2017-06-23 2017-Xudong-SMT/submit-ICTAC2017.tex
Improve the Algorithm 1.

@@
 	\If{Subnet is a pLTS}
-                \State $s$ is the local state of the pLTS in the global state $S$;
-		\For{each transition $tr$ starting from $s$}
-			\State apply Tr1 to build the corresponding
-                        $OT$; store $OT$ in $L$; \EndFor
+                \State Get the local state of the pLTS $s$ from $S$;
+		\For{each transition $tr$ starting from $s$} Apply Tr1
+			\State Build the corresponding
+                        $OT$; store $OT$ in $L$; 
+                 \EndFor
 	\EndIf
-	\If{Subnet is a pNet, apply Tr2:} 
-		\For{each $sv \in SV$}
+	\If{Subnet is a pNet}
+		\For{each $sv \in SV$} Apply Tr2
 			\State Invoke $Combining()$ to generate the
                         combination of sub-transitions, $Matching()$
-                        to match the combination with the $sv$; then
-                        store the result OTs in    $L$; 
+                        to match the combination with the $sv$; Store the result OTs in $L$; 
 		\EndFor

### 2017-09-27 2016-Weak-FH-Bisim/WeakBisim.tex
Rabea's file and comments

@@
 \newcommand{\LUDO}[1]{\textcolor{green}{#1}}
+\newcommand{\RAB}[1]{\textcolor{magenta}{#1}}
 \newcommand{\coloncolon}{{:\hspace{-.2ex}:}}
@@
 
+\RAB{La notation overline n'a pas ete introduite auparavant? Aussi, je n'ai pas trop bien saisi quand on utilise overline et la la notation k in K}
+
 A pNet $Q$ is \emph{closed} if it has no hole: $\Holes(Q)=\emptyset$; else it
@@
 \end{figure}
+
+\RAB{les notations des figures pretes a confusion: carre/carre arrondi et rond/triangle plein}
 
@@
 
+\RAB{d'ou vient l'action v? notation S\_j ou bien Sort\_j}
+
 \begin{example}\emph{An open-transition.}
@@
 
+\RAB{diff entre Leaves(p) et overline\{Leaves\}?}
+
 %% \begin{example} \emph{State of a pNet}
@@
 \end{array}\]
+
+\RAB{ce pred est-il diff de celui de la def 4?}
+
 In any other case (if the action families do not match or if there is no valuation of
@@
 	\begin{itemize}
-		\item $J$ is the indices of the holes: $Holes(p)= H_j^{j\in J}$.
+		\item $J$ is the indices of the holes: $Holes(p)= H_j^{j\in J}$. \RAB{Holes(p)= J en ref a page 4}
 		%  \item $\overline{L}^L = Leaves(p), \overline{H}^J = Holes(p)$
@@
 	%% 	think handling assignments is not trivial, even for comparisons of pLTSs. }
+
+\RAB{notation S, T or underline\{S\}, underline\{T\}? pas clair...}
 
@@
     $
+
+\RAB{que signifie notation uplus Post? Pourquoi fresh(v), et v existe satisfait Pred? aussi b\_j?}
 

### 2017-09-28 2016-Weak-FH-Bisim/WeakBisim.tex
partial

@@
 
-To have some practical interest, it is important to know when this
-algorithm terminates. The following theorem shows that an open-pNet
+Given an open-pNet
 with finite synchronisation sets, finitely many leaves and
 holes, and each pLTS at leaves having a finite number of states and
-(symbolic) transitions, has a finite automaton:
-
-\begin{theorem}[Finiteness of open-automata.]\\
-Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
-  J}$, if the sets $L$ and $J$ are finite, if the synchronisation vectors of all pNets 
-  included in  $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ 
-  are finite, and if
-$\forall i \in L.\, finite{(states(pLTS_i))} \text{ and } pLTS_i$
-has a finite number of state variables, then Algorithm 1 terminates
-and produces an open automaton 
-$\mathcal{T}$ with finitely many states and transitions.
+(symbolic) transitions, has a finite automaton (see \ref{Forte}).
+
+  \TODO{Eric: what is ``elimination of intermediate variables ?'' it
+    transforms the predicates, so I think it is not any kind of
+    ``equivalence'' transformation, rather some sort of
+    abstraction... Define... Does it change the satisfiability ?}
+
+%% \begin{theorem}[Finiteness of open-automata.]\\
+%% Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
+%%   J}$, if the sets $L$ and $J$ are finite, if the synchronisation vectors of all pNets 
+%%   included in  $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ 
+%%   are finite, and if
+%% $\forall i \in L.\, finite{(states(pLTS_i))} \text{ and } pLTS_i$
+%% has a finite number of state variables, then Algorithm 1 terminates
+%% and produces an open automaton 
+%% $\mathcal{T}$ with finitely many states and transitions.
 
@@
 %   \to finite{(\mathcal{T})}$$
-\end{theorem}
-
-\section{Tooling}
-
-\TODO{Eric: high level description of the implementation}
-
-\ERIC{
-=> Context VCE, ref to FASE paper\\
-=> Current prototype: programatic creation of pNet objects, through the pNet API in VCE. On the middle term, this should be compiled from some language or graphical formalism.\\
-=> Open transitions are computed as a direct implementation of the algorithm above.
-Steps 2a-2b are merged: at each pNet node, after application of rule Tr2, the resulting OT is built from the premisses, without explicitely constructing the deduction tree.
-\\
-=> Variable names are generated for all ``fresh'' and ``clone'' operations, using structured variable names ensuring uniqueness of fresh names, but also reasonable readability of these names for debugging purposes.\\
-=> Satisfiability check is done only at toplevel of the deduction tree construction.
-An alternative would be to submit the satisfiability check to the SMT solver at each level of the tree construction, potentialy reducing the overall number of combinations.
-But submission to the SMT engine is costly, and more complexity analysis is required before deciding if this would be worthwhile.\\
-=> Simplification is not yet implemented. It is not strictly required for the Open Automaton construction, but it will be critical later for predicate comparison in the bisimulation algorithm.}
+% \end{theorem}
 
@@
 that have indistinguishable behaviour, with respect to some definition
-of \emph{invisible actions} that are considered internal to some
+of \emph{internal actions} that are considered local to some
 subsystem, and consequently cannot be observed, nor used for
@@
 e.g. $tau$ in CCS, and $i$ in Lotos, we will rely here on some set of
-\emph{invisible actions} depending on a specific action algebra.
-
-\TODO{we should understand if it make sense to distinguish invisible
-  from synchronised actions: in the Forte paper we wrote ``using  as 
-\emph{invisible actions} a subset of the
-\emph{synchronised actions} defined in Section~\ref{section:pnets}''}.
+\emph{internal actions} depending on a specific action
+algebra. Naturely, an internal action cannot be synchronised with
+actions of other systems in its environment.
+
+%% \TODO{we should understand if it make sense to distinguish invisible
+%%   from synchronised actions: in the Forte paper we wrote ``using  as 
+%% \emph{invisible actions} a subset of the
+%% \emph{synchronised actions} defined in Section~\ref{section:pnets}''}.
 
@@
 \noindent
-Let $A_1$ and $A_2$ be open automata, and $mathcal{R}$ a relation over
+Let $A_1$ and $A_2$ be open automata, and $\mathcal{R}$ a relation over
 $S_1$ and $S_2$, as in Definition \ref{def-FH-bisim}.
@@
 whether two open pNets are bisimilar.
+
+\TODO{Eric: high level description of the implementation}
+
+\ERIC{
+=> Context VCE, ref to FASE paper\\
+=> Current prototype: programatic creation of pNet objects, through the pNet API in VCE. On the middle term, this should be compiled from some language or graphical formalism.\\
+=> Open transitions are computed as a direct implementation of the algorithm above.
+Steps 2a-2b are merged: at each pNet node, after application of rule Tr2, the resulting OT is built from the premisses, without explicitely constructing the deduction tree.
+\\
+=> Variable names are generated for all ``fresh'' and ``clone'' operations, using structured variable names ensuring uniqueness of fresh names, but also reasonable readability of these names for debugging purposes.\\
+=> Satisfiability check is done only at toplevel of the deduction tree construction.
+An alternative would be to submit the satisfiability check to the SMT solver at each level of the tree construction, potentialy reducing the overall number of combinations.
+But submission to the SMT engine is costly, and more complexity analysis is required before deciding if this would be worthwhile.\\
+=> Simplification is mostly implemented. It is not strictly required for the Open Automaton construction, but it will be critical later for predicate comparison in the bisimulation algorithm.}
 
@@
 To prove transitivity of strong FH-bisimulation on pNets it is sufficient to prove 
-transitivity of the strong FH-bisimulation on states. Consider 3 open automata 
+transitivity of the strong FH-bisimulation on states of their Open Automata. Consider 3 open automata 
 $\mathcal{T}_1$, $\mathcal{T}_2$, $\mathcal{T}_3$ and states $s^1$, $s^2$, $s^3$ in those 

### 2017-09-28 2016-Weak-FH-Bisim/WeakBisim.tex
Meeting corrections

--- 2017-09-27 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 \paragraph{Structure.}
+
+\section{Notations}
+
+\subsubsection{Syntax and Notations}
+\TODO{copy pasted -- rearrange + move?}
+
+In the following definitions, we extensively use indexed structures
+(maps) over some countable indexed sets. The indices will usually be
+integers, bounded or not. Such an indexed family is denoted as
+follows: $a_i^{i\in I}$ is a family of elements $a_i$ indexed over the
+set $I$. Such a family
+is equivalent to the mapping $(i\mapsto a_i)^{i\in I}$.
+To specify the set over which the structure is indexed, 
+indexed structures are always denoted with an exponent of the form $i\in I$
+(arithmetic only appears in the indexes if necessary).
+Consequently, $a_i^{i\in I}$ defines first $I$ the set over which the
+family is indexed, and then $a_i$ the elements of the family.
+
+For example $a^{i\in\{3\}}$ is
+the mapping with a single entry $a$ at index $3$; exceptionally, such mappings with
+only a few entries will also be denoted $(3\mapsto a)$.
+When this is not ambiguous, we shall use abusive vocabulary and
+notations for sets, and typically write ``indexed set over I'' when  
+formally we should speak of multisets, and ``$x\in
+A_i^{i\in I}$'' to mean $\exists i\in I.\, x=A_i$.
+An empty family is denoted $[]$. % (it can be defined as $a_i^{i\in\emptyset}$).
+To simplify equations, an indexed set can be denoted $\set{M}$
+instead of $M_l^{l\in L}$ when $L$ is irrelevant.
+
+Let $\uplus$ be the disjoint union operator on indexed sets. 
+The elements
+of the union are then accessed by using an index of one of the two
+joined families.
+We suppose here that disjoint unions are always well defined; this
+requires to choose disjoint  
+indices in the definition of the component system (e.g. name of
+methods of different interfaces).
+
+$\subst{y\gets x}$ is the substitution operation that replaces in a term all occurrences 
+of the term $y$ by the term $x$ (note that the absence of binders makes this operation 
+trivial).
 
@@
 
-\item[$\bullet$] $J\in\I_\P$ is the set over which holes are indexed.
-$I$ and $J$ are \emph{disjoint}: $I\cap J=\emptyset$,  $I\cup J\neq\emptyset$
+\item[$\bullet$] $J\!\in\!\I_\P$ is a set of indexes, called \emph{holes}.
+$I$ and $J$ are \emph{disjoint}: $I\!\cap\! J=\emptyset$,  $I\!\cup\! J\neq\emptyset$
 \item[$\bullet$] $S_j \subseteq \AlgAS$ is a set of action terms, denoting the $\Sort$ of
@@
 	hold \emph{after the open transition}, they are represented as a substitution of the 
-	form $\{x_k\gets e_k\}^{k\in K}$ 
+	form $\subst{x_k\gets e_k}^{k\in K}$ 
 	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
@@
 
+We define states of open pNets as tuples of states, where we denote tuples
+in structured states as $\triangleleft\ldots\triangleright$ for distinguishing tuple 
+states from other tuples.
 \begin{definition}[States of open pNets]\label{def-states}
   A state of an open pNet is a tuple (not necessarily finite) of the
-  states of its leaves (in which we denote tuples
-  in structured states as $\triangleleft\ldots\triangleright$ for better readability).
-
-  For any pNet p, let $\overline{Leaves} = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be the set of pLTS at its leaves,
+  states of its leaves.
+
+  For any pNet p, let $\Leaves(p) = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be 
+  the set of pLTS at its leaves,
   then $States(p) = \{\triangleleft s_i^{i\in L}
@@
 
+\TODO{say that This predicate entails a verification of satisfiability}
+
 \RAB{ce pred est-il diff de celui de la def 4?}
@@
 	\begin{itemize}
-		\item $J$ is the indices of the holes: $Holes(p)= H_j^{j\in J}$. \RAB{Holes(p)= J en ref a page 4}
+		\item $J$ is the set of holes: $Holes(p)= J$. \RAB{Holes(p)= J en ref a 
+		page 4}
 		%  \item $\overline{L}^L = Leaves(p), \overline{H}^J = Holes(p)$
-		\item $\overline{\mathcal{S}} = States(p)$ and $s_0 = InitState(p)$
+		\item ${\mathcal{S}} = States(p)$ and $s_0 = InitState(p)$
 		\item $\mathcal{T}$ is the smallest set of open transitions
@@
 
-	The rule for a pLTS $p$  checks that the guard 
+	The rule for a pLTS  checks that the guard 
 	is verified and transforms assignments into post-conditions:
@@
 					J}\rangle} s'\in \to  }
-		{ p = \mylangle  S,s_0, \to \myrangle
+		{ \mylangle  S,s_0, \to \myrangle
 			\models
@@
 	i.e. a flatten view of the pNet: e.g. $L$ is the index set of the
-	Leaves, $L_k$ the index set of the leaves of one subnet, so all $L_k$
+	Leaves, $L_m$ the index set of the leaves of one subnet indexed $m$, so all $L_m$
 	are disjoint subsets of $L$. Thus the states in the open transitions,
@@
     	{\ostate{s_{i}^{i \in L_m}} \xrightarrow {v_m}
-    		\ostate{s_{i}^{\prime\ i \in L_m}}}
+    		\ostate{(s_i^\prime)^{i\in L_m}}}
     	%\land
@@
     }
-    {p = \mylangle \pNet_i^{i\in I}, S_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle
+    {\mylangle \pNet_i^{i\in I}, S_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle
     	\models
@@
     		{\ostate{s_i^{i\in L}} \xrightarrow {v}
-    			\ostate{s_i^{\prime i\in L}}}
+    			\ostate{(s_i^\prime)^{i\in L}}}
     	}
@@
 
-Let $\mathcal{R}''$ be the relation: 
-\[\mathcal{R}'' = \Big\{(s^1,s^3|\Pred\,''\phi)\Big|
-\displaystyle\Pred\,''=\bigvee_{ \begin{array}{l}
-(s^1,s^2|\Pred)\in\mathcal{R}\\ (s^2,s^3|\Pred\,')\in\mathcal{R}' 	
+Let $\mathcal{R}''$ be the relation (We denote $\Phi$ a set of renamings):
+
+%\begin{mathpar}
+%\inferrule{}
+%{}
+%\end{mathpar}
+
+\[\mathcal{R}'' = \Big\{(s^1,s^3|\Pred\,'')\Big|
+\displaystyle
+ \begin{array}[t]{l}\exists (s^2_p)^{p\in P}.\,\exists (\Phi_p)^{p\in P}.\,\\
+\quad 
+	\big(\begin{array}{l}
+	\forall p\in P.\, (s^1,s^2_p|\Pred)\in\mathcal{R}\land 
+	(s^2_p,s^3|\Pred\,')\in\mathcal{R}'\land \\
+	 \forall\ \phi\in\Phi_p.\,
+	  \fv((\Pred\land\Pred')\phi)\subseteq \fv(\mathcal{T}_1)\cup\fv(\mathcal{T}_3) \land
+	  \dom(\phi)\subseteq \fv(\mathcal{T}_2)
 	\end{array}
-}\!\!\!\!\!\exists \phi.\begin{array}[t]{l} (\Pred\land\Pred\,')\phi\\
-\land \fv((\Pred\land\Pred)\phi)\subseteq \fv(\mathcal{T}_1)\cup\fv(\mathcal{T}_3)
-\\
-\land \dom(\phi)\subseteq \fv(\mathcal{T}_2)
-\end{array}\Big\}\]
-
-\TODO{is it satisfactory as a notion of transitive composition? It would be easy to 
-extend it a bit to allow having several substitutions for the same s2, eg one that works 
-for different values of variables in T1 and T3. It would make the notations more complex 
-but it would be OK. I do not think I can do more than that}
+	\big)\\
+\quad
+\land ~\Pred'' =\displaystyle\bigvee_{\begin{array}{l}
+	p\in P\\\phi\in \Phi_p
+	\end{array}} (\Pred\land\Pred\,')\phi
+
+\end{array}\Big\}
+\]
+%(s^1,s^2|\Pred)\in\mathcal{R}\\ (s^2,s^3|\Pred\,')\in\mathcal{R}' 	
+%}\!\!\!\!\!\exists \phi.\begin{array}[t]{l} \\
+%\land 
+%\\
+%\land 
+%\\
+\TODO{s2p is the family of states that relate s1 and s2 big phi is the set of renamings 
+for each s2 in the family}
 
@@
 values of $s^2$ are collected by a disjunction. 
-Finally, a substitution should ensure that the 
+Finally, a set of substitutions should ensure that the 
 free variables of the predicates are only the ones of $\mathcal{T}_1$ and 
-$\mathcal{T}_1$. This substitution somehow matches the two predicates by eliminating the 
-free variables.
+$\mathcal{T}_1$. These substitutions somehow express the different ways to match the two 
+predicates by eliminating the 
+free variables. We simplify the proof to the case where a single substitution is 
+necessary for each state $s^2$; the extension to a set of substitution is relatively 
+simple but complicates the notations. $\phi_p$ is this set of substitutions in the proof 
+below.
 
@@
 $(s^1,s^2_p|\Pred_p)\in\mathcal{R}$,  and $(s^2_p,s^3|\Pred\,'_p)\in\mathcal{R}$. 
-Additionally we have $\Pred\,'' = (\bigvee_{p\in P} \Pred_p\land\Pred_p\,'\phi_p)$.
+Additionally we have $\Pred\,'' = \bigvee_{p\in P} (\Pred_p\land\Pred_p)\,'\phi_p$.
 We have 

### 2017-09-28 2016-Weak-FH-Bisim/WeakBisim.tex
test
Sorts

@@
 A pNet is a hierarchical structure where leaves are pLTSs and holes:\\
-$\pNet\triangleq pLTS~|~\mylangle \pNet_i^{i\in I}, S_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle$
+$\pNet\triangleq pLTS~|~\mylangle \pNet_i^{i\in I}, Sort_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle$
 where
@@
 $I$ and $J$ are \emph{disjoint}: $I\!\cap\! J=\emptyset$,  $I\!\cup\! J\neq\emptyset$
-\item[$\bullet$] $S_j \subseteq \AlgAS$ is a set of action terms, denoting the $\Sort$ of
+\item[$\bullet$] $Sort_j \subseteq \AlgAS$ is a set of action terms, denoting the $\Sort$ of
 hole $j$.
@@
   I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$,  $\forall j\!\in\!
-  J_k.\,\alpha_{j}\!\in\!S_j$, and $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
+  J_k.\,\alpha_{j}\!\in\!Sort_j$, and $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
   J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
@@
 x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
-		J}\rangle} s'\in \to \} \\ \Sort(\mylangle
-\set{\pNet}, \set{\symb{S}}, \set{\symb{SV}}\myrangle) =\{\alpha'_k |\, \alpha_j^{j\in J_k}\to\alpha'_k\in\set{\symb{SV}}\}
+    J}\rangle} s'\in \to \} \\
+\Sort(\mylangle \pNet_i^{i\in I}\!,Sort_j^{j\in J}\!,
+\overline{\symb{SV}}\myrangle)
+=\{\alpha'_k |\, \alpha_j^{j\in J_k}\to\alpha'_k\in\set{\symb{SV}}\}
 \end{array}
@@
 \Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset \\
-\Holes(\mylangle \pNet_i^{i\in I}\!,S_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) =J\cup{\displaystyle \bigcup_{i\in I}\Holes(\pNet_i)}\\
+\Holes(\mylangle \pNet_i^{i\in I}\!,Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) =J\cup{\displaystyle \bigcup_{i\in I}\Holes(\pNet_i)}\\
 \forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
@@
 \Leaves(\mylangle S,s_0, \to\myrangle) \!=\! \{ \mylangle S,s_0, \to\myrangle \}\\
-\Leaves(\mylangle \pNet_i^{i\in I}\!,S_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \bigcup_{i\in I}\Leaves(\pNet_i)}
+\Leaves(\mylangle \pNet_i^{i\in I}\!,Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \bigcup_{i\in I}\Leaves(\pNet_i)}
 \end{array}\]
@@
         is a transition of the hole $j$, for any action $b_j$ in the
-        sort $Sort_j$. \Pred\ is a predicate
+        sort $Sort_j$. $v$ is a variable denoting the resulting action
+        of this open transition. \Pred\ is a predicate 
 	over the different variables of the
@@
 \end{definition}
-
-\RAB{d'ou vient l'action v? notation S\_j ou bien Sort\_j}
 
@@
 Let
-$\mylangle\overline{\pNet},\overline{S},\symb{SV}_k^{k\in K} \myrangle$
+$\mylangle\overline{\pNet},\overline{Sort},\symb{SV}_k^{k\in K} \myrangle$
 be a pNet. Consider a synchronisation vector $SV_k$, for $k\in K$. We define a
@@
     }
-    {\mylangle \pNet_i^{i\in I}, S_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle
+    {\mylangle \pNet_i^{i\in I}, Sort_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle
     	\models
@@
 prove that it is decidable whether a relation is a 
-FH-bisimulation provided the logic of the predicates is decidable (see
+FH-bisimulation, provided the logic of the predicates is decidable (see
 \cite{henrio:Forte2016}). }
@@
 \begin{definition}[pNet composition]
-	An open pNet: $\pNet = \mylangle \pNet_i^{i\in I}, S_j^{j\in J}, 
+	An open pNet: $\pNet = \mylangle \pNet_i^{i\in I}, Sort_j^{j\in J}, 
 	\overline{\symb{SV}}\myrangle$
@@
 	\[\pNet\left[\pNet'\right]_{j_0}= \mylangle 
-	\pNet_i^{i\in I}\uplus\{j_0\mapsto \pNet'\},S_j^{j\in J\setminus \{j_0\}},
+	\pNet_i^{i\in I}\uplus\{j_0\mapsto \pNet'\},Sort_j^{j\in J\setminus \{j_0\}},
 	\overline{\symb{SV}}\myrangle
@@
 	Consider an open pNet:
-	$\pNet = \mylangle \pNet_i^{i\in I}, S_j^{j\in J}, 
+	$\pNet = \mylangle \pNet_i^{i\in I}, Sort_j^{j\in J}, 
 	\overline{\symb{SV}}\myrangle$.
 	Let $j_0\in J$ be a hole. Let $Q$ and $Q'$ be two FH-bisimilar pNets such that 
-	$\Sort(Q)=\Sort(Q')=S_{j_0}$\footnote{Note that $\Sort(Q)=\Sort(Q')$ is ensured by 
-	stronfg bisimilarity.}. Then 
+	$\Sort(Q)=\Sort(Q')=Sort_{j_0}$\footnote{Note that $\Sort(Q)=\Sort(Q')$ is ensured by 
+	strong bisimilarity.}. Then 
 	$\pNet[Q]_{j_0}$ and 
@@
 	Consider two FH-bisimilar open pNets:
-	$\pNet = \mylangle \pNet_i^{i\in I}, S_j^{j\in J}, 
+	$\pNet = \mylangle \pNet_i^{i\in I}, Sort_j^{j\in J}, 
 	\overline{\symb{SV}}\myrangle$ and 	$\pNet' = \mylangle {\pNet'}_i^{i\in I}, 
-	S_j^{j\in 
+	Sort_j^{j\in 
 	J}, 	\overline{\symb{SV'}}\myrangle$ 
 	(recall they must have the same holes to be bisimilar).
-	Let $j_0\in J$ be a hole, and $Q$ be a pNet such that $\Sort(Q)=S_{j_0}$. Then $\pNet[Q]_{j_0}$ and 
+	Let $j_0\in J$ be a hole, and $Q$ be a pNet such that $\Sort(Q)=Sort_{j_0}$. Then $\pNet[Q]_{j_0}$ and 
 	$\pNet'[Q]_{j_0}$ are FH-bisimilar.
@@
 	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose:
-	\[ P[Q]_{j_0}   % = \mylangle \pNet_i^{i\in I}, S_j^{j\in J}, 
-	%\symb{SV}_k^{k\inK}\myrangle
+	\[ P[Q]_{j_0}  
 		\models
@@
 Then, we have\\[-2ex]
-	\[ P[Q]_{j_0}   % = \mylangle \pNet_i^{i\in I}, S_j^{j\in J}, 
-	%\symb{SV}_k^{k\inK}\myrangle
+	\[ P[Q]_{j_0}  
 	\models
@@
 			$b_{j x}=b_j$):\\[-2ex]
-				\[ P'[Q]_{j_0}   % = \mylangle \pNet_i^{i\in I}, S_j^{j\in J}, 
-				%\symb{SV}_k^{k\inK}\myrangle
+				\[ P'[Q]_{j_0}   
 				\models
@@
 \section{Discussion on substitution, matching, unification}
-
-\TODO{I think appendices B and C must be removed from the submission
-  (;-). Do we need anything else as an appendix ? Maybe some of the
-  details on Hierarchical Braodcast, when we will deal with the space limit...}
 

### 2017-09-29 2016-Weak-FH-Bisim/WeakBisim.tex
test
back to the old proof ; but with fresh variable arguments

@@
        	}
+%       \begin{proof}
+%
+%       It is trivial to check reflexivity and symmetry. Here we focus on the
+%transitivity. 
+%To prove transitivity of strong FH-bisimulation on pNets it is sufficient to prove 
+%transitivity of the strong FH-bisimulation on states of their Open Automata. Consider 3 
+%open automata 
+%$\mathcal{T}_1$, $\mathcal{T}_2$, $\mathcal{T}_3$ and states $s^1$, $s^2$, $s^3$ in 
+%those 
+%automata\footnote{We omit the constraints stating that each $s^i_x$ is in the states of 
+%$\mathcal{T}_i$ for the sake of readability}.
+%Suppose we have $\mathcal{R}$ an FH-bisimulation relation between states of 
+%$\mathcal{T}_1$ and of  $\mathcal{T}_2$; members of $\mathcal{R}$ are of the form 
+%$(s^1,s^2|\Pred)$.
+%Suppose we also  have $\mathcal{R}'$ an FH-bisimulation relation between states of 
+%$\mathcal{T}_2$ and of  $\mathcal{T}_3$; members of $\mathcal{R}2$ are of the form 
+%$(s^2,s^3|\Pred\,')$.
+%We use $\fv$ a function returning the free variables of a term/automaton.
+%
+%Let $\mathcal{R}''$ be the relation (We denote $\Phi$ a set of renamings): 
+%
+%%\begin{mathpar}
+%%\inferrule{}
+%%{}
+%%\end{mathpar}
+%
+%\[\mathcal{R}'' = \Big\{(s^1,s^3|\Pred\,'')\Big|
+%\displaystyle
+% \begin{array}[t]{l}\exists (s^2_p)^{p\in P}.\,\exists (\Phi_p)^{p\in P}.\,\\
+%\quad 
+%	\big(\begin{array}{l}
+%	\forall p\in P.\, (s^1,s^2_p|\Pred)\in\mathcal{R}\land 
+%	(s^2_p,s^3|\Pred\,')\in\mathcal{R}'\land \\
+%	 \forall\ \phi\in\Phi_p.\,
+%	  \fv((\Pred\land\Pred')\phi)\subseteq \fv(\mathcal{T}_1)\cup\fv(\mathcal{T}_3) \land
+%	  \dom(\phi)\subseteq \fv(\mathcal{T}_2)
+%	\end{array}
+%	\big)\\
+%\quad
+%\land ~\Pred'' =\displaystyle\bigvee_{\begin{array}{l}
+%	p\in P\\\phi\in \Phi_p
+%	\end{array}} (\Pred\land\Pred\,')\phi
+%	
+%\end{array}\Big\}
+%\]
+%%(s^1,s^2|\Pred)\in\mathcal{R}\\ (s^2,s^3|\Pred\,')\in\mathcal{R}' 	
+%%}\!\!\!\!\!\exists \phi.\begin{array}[t]{l} \\
+%%\land 
+%%\\
+%%\land 
+%%\\
+%\TODO{s2p is the family of states that relate s1 and s2 big phi is the set of renamings 
+%for each s2 in the family}
+%
+%The relation is built as follows: for each pair of state $s^1$, $s^3$, for each state 
+%$s^2$ such that $\mathcal{R}$ relates $s^1$ and $s^2$, and $\mathcal{R}'$ relates $s^2$ 
+%and $s^3$, we take the conjunction of the two predicates. The predicates for different 
+%values of $s^2$ are collected by a disjunction. 
+%Finally, a set of substitutions should ensure that the 
+%free variables of the predicates are only the ones of $\mathcal{T}_1$ and 
+%$\mathcal{T}_1$. These substitutions somehow express the different ways to match the two 
+%predicates by eliminating the 
+%free variables. We simplify the proof to the case where a single substitution is 
+%necessary for each state $s^2$; the extension to a set of substitution is relatively 
+%simple but complicates the notations. $\phi_p$ is this set of substitutions in the proof 
+%below.
+%
+% We will show
+%that $\mathcal{R}''$ is an FH-bisimulation. Consider 
+%$(s^1,s^3|\Pred\,'')\in\mathcal{R}''$. Then there is a set of states of 
+%$\mathcal{T}_2$ relating $s^1$ and $s^3$, let $(s^2_p)^{p\in P}$ be this family.  
+%For any $p\in P$ by definition of $\mathcal{R}''$,
+%$(s^1,s^2_p|\Pred_p)\in\mathcal{R}$,  and $(s^2_p,s^3|\Pred\,'_p)\in\mathcal{R}$. 
+%Additionally we have $\Pred\,'' = \bigvee_{p\in P} (\Pred_p\land\Pred_p)\,'\phi_p$.
+%We have 
+%the 
+%following by definition of bisimulation.
+%For any open transition $OT$ in $\mathcal{T}_1$ originating from $s^1$:
+%
+%\begin{mathpar}
+%
+%\inferrule*[myfraction=\reddottedrule]
+%{\{s^1_i\xrightarrow{a_i}_i {s^{1}}'_i\}^{i\in I_1}, % , s^1_i,s^{1'}_i\in
+%	%States(I_1)
+%	\{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
+%{s^1 \xrightarrow {v} {s^{1}}'}
+%
+%\end{mathpar}
+%
+%there exist open transitions $OT_{p x}^{x\in X} \subseteq \mathcal{T}_2$:
+%
+%\begin{mathpar}
+%
+%%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
+%\inferrule*[myfraction=\reddottedrule]
+%{\{s^{2}_{pi}\xrightarrow{a_{p i x}}_i s^{2}_{p i x}\}^{i\in I_{2 p x}},
+%	\{\xrightarrow{b_{j p x}}_j\}^{j\in J_{2px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
+%{s^2_p \xrightarrow {v_{px}} s^{2}_{px}}
+%%         \right)
+%\end{mathpar}
+%
+%such that  $\forall x, J_1=J_{2px}, (s^{1'},s^{2}_{px}|\Pred_{target_{px}})\in 
+%\mathcal{R}$;
+%and  \\
+%
+%$\Pred_p \land \Pred_{OT}\\
+%\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
+%\left( \forall j. b_j=b_{jpx}  \Rightarrow \Pred_{OT_{px}}
+%\land v\!=\!v_{px} \land
+%\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)$
+%
+%for any open transition $OT_{px}$, since
+%$(s^2_p,s^3|\Pred\,^\prime_p)\in\mathcal{R}'$ there exist open transitions
+%$OT_{pxy}^{x\in X, y\in Y} \subseteq \mathcal{T}_3$: 
+%
+%\begin{mathpar}
+%
+%%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
+%\inferrule*[myfraction=\reddottedrule]
+%{\{s^{3}_i\xrightarrow{a_{i p x y}}_i s^{3}_{i p x y}\}^{i\in I_{3 p x y}},
+%	\{\xrightarrow{b_{j p x y}}_j\}^{j\in J_{3pxy}}, \Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
+%{s^3 \xrightarrow {v_{pxy}} s^{3}_{pxy}}
+%%         \right)
+%
+%\end{mathpar}
+%such that  $\forall y, J_{2px}=J_{3pxy}, 
+%(s^{2}_x,s^{3}_{pxy}|\Pred_{target_{pxy}})\in \mathcal{R}'$; and  \\
+%$\Pred\,'_p \land \Pred_{OT_{px}}\\
+%\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
+%\left( \forall j. b_{jpx}=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
+%\land v_{px}\!=\!v_{pxy} \land
+%\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.
+%
+%This is verified for each $p\in P$. Overall,  we have a family of open transitions 
+%$OT_{pxy}^{p\in 
+%P, x\in X, 
+%y\in Y} \subseteq \mathcal{T}_3$ that should simulate \emph{OT}.
+%
+%First, $\forall y, \forall x, \forall p, J_1=J_{2px}=J_{3pxy}, 
+%({s^{1}}',s^{3}_{pxy}|\Pred\,'_{target_{pxy}})\in \mathcal{R}''$. 
+%Indeed for any 
+%$p$, 
+%$x$, and 
+%$y$, $s^2_{px}$
+%relate ${s^{1}}'$ and $s^{3}_{pxy}$, indeed
+%$(s^{1'},s^{2}_{px}|\Pred_{target_{px}})\in \mathcal{R}$
+% and $(s^{2}_x,s^{3}_{pxy}|\Pred_{target_{pxy}})\in \mathcal{R}'$. 
+% More precisely, $s^{2}_{px} \in ({s^{2}_p}')^{p\in P'}$ where $({s^{2}_p}')^{p\in 
+% P'}$ 
+% is 
+% the set of states relating ${s^{1}}'$ and $s^{3}_{pxy}$.
+%Consequently, for all $p$, $x$, $y$,\\
+% $\left(\exists \phi'.\,(\Pred_{target_{px}}\land 
+%\Pred_{target_{pxy}})\phi'\land \fv((\Pred\land\Pred)\phi')\subseteq 
+%\fv(\mathcal{T}_1)\cup\fv(\mathcal{T}_3)\right)\implies 
+%\Pred\,'_{target_{pxy}}$ \\
+%This is one element of the  disjunction defining the 
+%predicate 
+%relating ${s^{1}}'$ and $s^{3}_{pxy}$ in the definition of $\mathcal{R}''$.
+%
+%Second, we need \\
+%\begin{small}
+%$\Pred\,'' \land \Pred_{OT}\\
+%\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
+%\left( \forall j. b_j=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
+%\land v\!=\!v_{pxy} \land
+%\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
+%\end{small}
+%
+%We have, for all $p$
+%\begin{small}
+%$\Pred_p \land \Pred_{OT}\land\Pred'_p\\
+%\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
+%\left( \forall j. b_j=b_{jpx}  \Rightarrow \Pred_{OT_{px}}
+%\land v\!=\!v_{px} \land
+%\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\land\Pred'_p\\
+%%
+%\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
+%\left( \forall j. b_j=b_{jpx}  \Rightarrow (\Pred_{OT_{px}}\land\Pred'_p)
+%\land v\!=\!v_{px} \land
+%\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\\
+%%
+%\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
+%\big( \forall j. b_j=b_{jpx}  \Rightarrow (\bigvee_{y\in Y} 
+%\big( \forall j'. b_{j'px}=b_{j'pxy}  \Rightarrow \Pred_{OT_{pxy}}
+%\land v_{px}\!=\!v_{pxy}\\\hspace{3em}~ \land
+%\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\big))
+%\land v\!=\!v_{px} \land
+%\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\\
+%%
+%\hspace{1cm} \implies\!\!\! \bigvee_{x\in X} \bigvee_{y\in Y}
+%\big( \forall j, j'. b_j=b_{jpx} \land b_{j'px}=b_{j'pxy}
+%\Rightarrow \big( 
+%\Pred_{OT_{pxy}}
+%\land v\!=v_{px}\!=\!v_{pxy}\\\hspace{3em}~ \land
+%\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}
+% \land
+%\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\big)
+%$
+%
+%\end{small}
+%
+%Additionally, the Post substitutions only have an effect on the  predicates that  use 
+%some of the 
+%substituted 
+%variables, and because of the domain of the substitutions we have:\\
+%$(\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\land 
+%\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}})\phi\\
+%%
+%= 
+%(\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land
+%\Pred_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}) 
+%\phi\\
+%%
+%= 
+%((\Pred_{target_{px}}\land
+%\Pred_{target_{pxy}})\subst{\Post_{OT_{px}}}\phi) 
+%\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\\
+%%
+%\implies\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}
+%\subst{\Post_{OT_{pxy}}}\\
+% $
+%Finally, gathering the previous results, and using the fact that only variables of 
+%$\mathcal{T}_2$ are changed by $\phi$ substitutions:
+%
+%$\Pred\,'' \land \Pred_{OT}\\
+%\hspace{1cm} \implies\!\!\! \bigvee_{p\in P}(\Pred_p \land 
+%\Pred_{OT}\land\Pred\,'_p)\phi\\
+%\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
+%\left( \forall j. b_j=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
+%\land v\!=\!v_{pxy} \land
+%\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)
+%$
+%
+%This is the expected property.
+%
+%
+%\smallskip
+%Concerning the other direction of bisimulation, it is sufficient to notice that the role 
+%of $s^1$ and $s^3$ in the definition of $\mathcal{R}''$ is symmetrical, and thus the 
+%proof is similar.
+%
+%       \end{proof}
+%       
+%       \bigskip
+%       
+%       
               \begin{proof}
@@
        	transitivity. 
-To prove transitivity of strong FH-bisimulation on pNets it is sufficient to prove 
-transitivity of the strong FH-bisimulation on states of their Open Automata. Consider 3 open automata 
-$\mathcal{T}_1$, $\mathcal{T}_2$, $\mathcal{T}_3$ and states $s^1$, $s^2$, $s^3$ in those 
-automata\footnote{We omit the constraints stating that each $s^i_x$ is in the states of 
+       	To prove transitivity of strong FH-bisimulation on pNets it is sufficient to 
+       	prove 
+       	transitivity of the strong FH-bisimulation on states. Consider 3 open automata 
+       	$\mathcal{T}_1$, $\mathcal{T}_2$, $\mathcal{T}_3$ and states $s^1$, $s^2$, $s^3$ 
+       	in those 
+       	automata\footnote{We omit the constraints stating that each $s^i_x$ is in the 
+       	states of 
        		$\mathcal{T}_i$ for the sake of readability}.
@@
        	$(s^1,s^2|\Pred)$.
-Suppose we also  have $\mathcal{R}'$ an FH-bisimulation relation between states of 
-$\mathcal{T}_2$ and of  $\mathcal{T}_3$; members of $\mathcal{R}2$ are of the form 
+       	Suppose we also  have $\mathcal{R}'$ an FH-bisimulation relation between states 
+       	of 
+       	$\mathcal{T}_2$ and of  $\mathcal{T}_3$; members of $\mathcal{R}2$ are of the 
+       	form 
        	$(s^2,s^3|\Pred\,')$.
-We use $\fv$ a function returning the free variables of a term/automaton.
-
-Let $\mathcal{R}''$ be the relation (We denote $\Phi$ a set of renamings):
-
-%\begin{mathpar}
-%\inferrule{}
-%{}
-%\end{mathpar}
-
-\[\mathcal{R}'' = \Big\{(s^1,s^3|\Pred\,'')\Big|
-\displaystyle
- \begin{array}[t]{l}\exists (s^2_p)^{p\in P}.\,\exists (\Phi_p)^{p\in P}.\,\\
-\quad 
-	\big(\begin{array}{l}
-	\forall p\in P.\, (s^1,s^2_p|\Pred)\in\mathcal{R}\land 
-	(s^2_p,s^3|\Pred\,')\in\mathcal{R}'\land \\
-	 \forall\ \phi\in\Phi_p.\,
-	  \fv((\Pred\land\Pred')\phi)\subseteq \fv(\mathcal{T}_1)\cup\fv(\mathcal{T}_3) \land
-	  \dom(\phi)\subseteq \fv(\mathcal{T}_2)
+
+       	Let $\mathcal{R}''$ be the relation: 
+       	\[\mathcal{R}'' = \{(s^1,s^3|\Pred\,'')|\,\Pred\,''=\bigvee_{ \begin{array}{l}
+       		(s^1,s^2|\Pred)\in\mathcal{R}\\ (s^2,s^3|\Pred\,')\in\mathcal{R}' 	
        		\end{array}
-	\big)\\
-\quad
-\land ~\Pred'' =\displaystyle\bigvee_{\begin{array}{l}
-	p\in P\\\phi\in \Phi_p
-	\end{array}} (\Pred\land\Pred\,')\phi
-
-\end{array}\Big\}
-\]
-%(s^1,s^2|\Pred)\in\mathcal{R}\\ (s^2,s^3|\Pred\,')\in\mathcal{R}' 	
-%}\!\!\!\!\!\exists \phi.\begin{array}[t]{l} \\
-%\land 
-%\\
-%\land 
-%\\
-\TODO{s2p is the family of states that relate s1 and s2 big phi is the set of renamings 
-for each s2 in the family}
-
-The relation is built as follows: for each pair of state $s^1$, $s^3$, for each state 
-$s^2$ such that $\mathcal{R}$ relates $s^1$ and $s^2$, and $\mathcal{R}'$ relates $s^2$ 
-and $s^3$, we take the conjunction of the two predicates. The predicates for different 
+       	}\,\Pred\land\Pred\,'\}\]
+
+       	The relation is built as follows: for each pair of state $s^1$, $s^3$, for each 
+       	state 
+       	$s^2$ such that $\mathcal{R}$ relates $s^1$ and $s^2$, and $\mathcal{R}'$ relates 
+       	$s^2$ 
+       	and $s^3$, we take the conjunction of the two predicates. The predicates for 
+       	different 
        	values of $s^2$ are collected by a disjunction.
-Finally, a set of substitutions should ensure that the 
-free variables of the predicates are only the ones of $\mathcal{T}_1$ and 
-$\mathcal{T}_1$. These substitutions somehow express the different ways to match the two 
-predicates by eliminating the 
-free variables. We simplify the proof to the case where a single substitution is 
-necessary for each state $s^2$; the extension to a set of substitution is relatively 
-simple but complicates the notations. $\phi_p$ is this set of substitutions in the proof 
-below.
 
@@
        	$\mathcal{T}_2$ relating $s^1$ and $s^3$, let $(s^2_p)^{p\in P}$ be this family.
+
        	For any $p\in P$ by definition of $\mathcal{R}''$,
        	$(s^1,s^2_p|\Pred_p)\in\mathcal{R}$,  and $(s^2_p,s^3|\Pred\,'_p)\in\mathcal{R}$. 
-Additionally we have $\Pred\,'' = \bigvee_{p\in P} (\Pred_p\land\Pred_p)\,'\phi_p$.
        	We have 
@@
        	For any open transition $OT$ in $\mathcal{T}_1$ originating from $s^1$:
-
+       	Additionally we have $\Pred\,'' = \bigvee_{p\in P} \Pred_p\land\Pred_p\,'$.
        	\begin{mathpar}
@@
        	{\{s^{3}_i\xrightarrow{a_{i p x y}}_i s^{3}_{i p x y}\}^{i\in I_{3 p x y}},
-	\{\xrightarrow{b_{j p x y}}_j\}^{j\in J_{3pxy}}, \Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
+       		\{\xrightarrow{b_{j p x y}}_j\}^{j\in J_{3pxy}}, 
+       		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
        	{s^3 \xrightarrow {v_{pxy}} s^{3}_{pxy}}
@@
        	(s^{2}_x,s^{3}_{pxy}|\Pred_{target_{pxy}})\in \mathcal{R}'$; and  \\
-$\Pred\,'_p \land \Pred_{OT_{px}}\\
+       	$\Pred\,'_p \land \Pred_{OT_x}\\
        	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
@@
 
-This is verified for each $p\in P$. Overall,  we have a family of open transitions 
+       	This is verified for each $p\in P$. Overall,  we have a family of open 
+       	transitions 
        	$OT_{pxy}^{p\in 
@@
        		y\in Y} \subseteq \mathcal{T}_3$ that should simulate \emph{OT}.
+
+		One can notice that, as bisimulation predicates are used to relate states that 
+		belong to two different open automata, the free variables of these predicates 
+		that do not belong to the two related automata can safely be renamed to avoid any 
+		name clash. In practice,
+       	we can suppose that, as $\Pred\,'_{target_{pxy}}$ is used to relate states of 
+       	$\mathcal{T}_1$, and $\mathcal{T}_3$, there exists a predicate obtained by 
+       	renaming variables, that is equivalent to $\Pred\,'_{target_{pxy}}$ and does not 
+       	contain the variables of 	$\mathcal{T}_2$. This predicate with ``fresh'' 
+       	variables is called   $\Pred\,'_{target_{pxy}}$ in the following.
+       	Similarly, we can suppose that $\Pred_{target_{px}}$ contains no 
+       	variable in $\mathcal{T}_3$, and $\Pred_{target_{pxy}}$ contains no 
+       	variable in $\mathcal{T}_1$.
 
@@
        	the set of states relating ${s^{1}}'$ and $s^{3}_{pxy}$.
-Consequently, for all $p$, $x$, $y$,\\
- $\left(\exists \phi'.\,(\Pred_{target_{px}}\land 
-\Pred_{target_{pxy}})\phi'\land \fv((\Pred\land\Pred)\phi')\subseteq 
-\fv(\mathcal{T}_1)\cup\fv(\mathcal{T}_3)\right)\implies 
-\Pred\,'_{target_{pxy}}$ \\
-This is one element of the  disjunction defining the 
+       	Consequently, for all $p$, $x$, $y$, $\Pred_{target_{px}}\land 
+       	\Pred_{target_{pxy}}\implies 
+       	\Pred\,'_{target_{pxy}}$ (this is one element of the  disjunction defining the 
        	predicate 
-relating ${s^{1}}'$ and $s^{3}_{pxy}$ in the definition of $\mathcal{R}''$.
+       	relating ${s^{1}}'$ and $s^{3}_{pxy}$ in the definition of $\mathcal{R}''$).
 
@@
 
-Additionally, the Post substitutions only have an effect on the  predicates that  use 
-some of the 
-substituted 
-variables, and because of the domain of the substitutions we have:\\
-$(\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\land 
-\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}})\phi\\
-%
+By construction, the Post substitutions only have an effect on the  
+variables of the open automaton they belong to, they also produce terms containing only 
+variables of the open automaton they belong to. Finally, because of the domain of the 
+substitutions  and of the predicates, we have:\\
+       	$\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\land 
+       	\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
        	= 
-(\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land
-\Pred_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}) 
-\phi\\
-%
-= 
-((\Pred_{target_{px}}\land
-\Pred_{target_{pxy}})\subst{\Post_{OT_{px}}}\phi) 
-\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\\
-%
-\implies\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}
-\subst{\Post_{OT_{pxy}}}\\
- $
-Finally, gathering the previous results, and using the fact that only variables of 
-$\mathcal{T}_2$ are changed by $\phi$ substitutions:
-
+       	\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land
+       	\Pred_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
+       	\implies\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
+       	= \Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}} $
+
+       	This allows us to conclude, with $\Pred\,'' = \bigvee_{p\in P} 
+       	\Pred_p\land\Pred_p\,'$:
+         	\begin{small}     	
 $\Pred\,'' \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \bigvee_{p\in P}(\Pred_p \land 
-\Pred_{OT}\land\Pred\,'_p)\phi\\
+\hspace{1cm} \implies\!\!\! \bigvee_{p\in P} (
+\Pred_p\land\Pred_p\,' \land \Pred_{OT})\\
+\hspace{1cm} \implies\!\!\!\bigvee_{p\in P}
+ \bigvee_{x\in X} \bigvee_{y\in Y}
+\big( \forall j, j'. b_j=b_{jpx} \land b_{j'px}=b_{j'pxy}
+\Rightarrow \big( 
+\Pred_{OT_{pxy}}
+\land v\!=v_{px}\!=\!v_{pxy}\\~\hspace{3em}~ \land
+\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\big)\big)
+\\
 \hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
@@
 \land v\!=\!v_{pxy} \land
-\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)
-$
-
-This is the expected property.
+\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
+  \end{small}
 
        	\smallskip
-Concerning the other direction of bisimulation, it is sufficient to notice that the role 
-of $s^1$ and $s^3$ in the definition of $\mathcal{R}''$ is symmetrical, and thus the 
+       	Concerning the other direction of bisimulation, it is sufficient to notice that 
+       	the role 
+       	of $s^1$ and $s^3$ in the definition of $\mathcal{R}''$ is symmetrical, and thus 
+       	the 
        	proof is similar.
@@
        \end{proof}
-
-       \bigskip
 

### 2017-09-29 2016-Weak-FH-Bisim/WeakBisim.tex
a small text for explaining transitivity rule ... not final

@@
 	\begin{itemize}
-		\item $J$ is the set of holes: $Holes(p)= J$. \RAB{Holes(p)= J en ref a 
-		page 4}
+		\item $J$ is the set of holes: $Holes(p)= J$. 
 		%  \item $\overline{L}^L = Leaves(p), \overline{H}^J = Holes(p)$
@@
        	}
+%%% A PROOF WITH CONSTRUCTIVE AERGUMENTS BUT THAT DOES NOT WORK
+
 %       \begin{proof}
@@
        	}\,\Pred\land\Pred\,'\}\]
+
+This relation is the adaptation of the transitivity to the conditional relationship that 
+defines a bisimulation. Indeed the global disjunction together with the conjuction of 
+predicates plays exactly the role of the intermediate element in a transitivity rule: 
+``there exists an intermediate state'' corresponds to the global disjunction, and the 
+conjunction of states expresses the intermediate predicate is used to ensure 
+satisfiability of the predicate relating the first state to the last one..
 

### 2017-10-04 2016-Weak-FH-Bisim/WeakBisim.tex
Remplacement Predsv + nettoyage des RAB
minor change
Back to rabea's merge
minor change again
notations

@@
 methods of different interfaces).
-
-$\subst{y\gets x}$ is the substitution operation that replaces in a term all occurrences 
+We denote $y\gets x$ a substitution. Application of the substitution is denoted
+$\subst{y\gets x}$, the operation replaces in a term all occurrences 
 of the term $y$ by the term $x$ (note that the absence of binders makes this operation 
@@
 	hold \emph{after the open transition}, they are represented as a substitution of the 
-	form $\subst{x_k\gets e_k}^{k\in K}$ 
+	form $\{x_k\gets e_k\}^{k\in K}$ 
 	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
@@
 
-\RAB{diff entre Leaves(p) et overline\{Leaves\}?}
-
 %% \begin{example} \emph{State of a pNet}
@@
 the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
-\[\Pred(SV_k, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow
+\[\Pred_{\symb{sv}}(SV_k, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow
 \begin{array}{l}
@@
 \TODO{say that This predicate entails a verification of satisfiability}
-
-\RAB{ce pred est-il diff de celui de la def 4?}
 
@@
 	\label{def:operationalSemantics}
-	The semantics of a pNet $p$ is an open automaton $A = <Leaves(p),J,\mathcal{S}, s_0,
-	\mathcal{T}>$ where:
-	\begin{itemize}
-		\item $J$ is the set of holes: $Holes(p)= J$. 
+	The semantics of a pNet $p$ is an open automaton $A = <Leaves(p),Holes(p),States(p),InitState(p),
+	\mathcal{T}>$ where $\mathcal{T}$ is the smallest set of open transitions		satisfying the rules below:
+%	\begin{itemize}
+%		\item $J$ is the set of holes: $Holes(p)= J$. 
 		%  \item $\overline{L}^L = Leaves(p), \overline{H}^J = Holes(p)$
-		\item ${\mathcal{S}} = States(p)$ and $s_0 = InitState(p)$
-		\item $\mathcal{T}$ is the smallest set of open transitions
-		satisfying the rules below:
-	\end{itemize}
+%		\item ${\mathcal{S}} = States(p)$ and $s_0 = InitState(p)$
+%		\item $\mathcal{T}$ is the smallest set of open transitions		satisfying the rules below:
+%	\end{itemize}
 
@@
 	%% 	think handling assignments is not trivial, even for comparisons of pLTSs. }
-
-\RAB{notation S, T or underline\{S\}, underline\{T\}? pas clair...}
 
@@
     $\inferrule
-    {k\!\in\! K \\ SV\!\!= \!clone(SV_k) \!=\! \alpha_m^{m \in I_k\uplus J_k} \!\to\! 
+    {k\!\in\! K \\ SV\!\!= \!{\tt clone}(SV_k) \!=\! \alpha_m^{m \in I_k\uplus J_k} \!\to\! 
     \alpha'_k \\
@@
     	\Pred = \bigwedge_{m\in I_k}\!\! \Pred_m \land
-    	\Pred(SV,a_i^{i\in I_k},b_j^{j\in J_k},v)\\
+    	\Pred_{\symb{sv}}(SV,a_i^{i\in I_k},b_j^{j\in J_k},v)\\
     	\forall j\!\!\in\!\! J_k. {\tt 
@@
     $
-
-\RAB{que signifie notation uplus Post? Pourquoi fresh(v), et v existe satisfait Pred? aussi b\_j?}
 
@@
 
+\RAB{Exemple a revoir. Les regles ne passent...}
+
 Note that while the scenario above is expressed as a single
@@
  transitions, but also as a reference to the work of De Simone~\cite{deSimone85},
- that pioneered this idea. Formally:
-
+ that pioneered this idea.\\
+\TODO{To check:}
+Let \ERIC{$\mathcal{R}=\{(s^1,s^2|\Pred_{s^1,s^2})\}$} be a relation over the set $\mathcal{S}_1$ and $\mathcal{S}_2$ constrained by a predicate
+More precisely, for any pair $(s^1,s^2)$, there is a 
+   single
+      $(s^1,s^2|\Pred_{s^1,s^2})\in\mathcal{R}$  stating that $s^1$ and $s^2$ are related if $\Pred_{s^1,s^2}$\ 
+      is 
+      true.
+
+\RAB{ I propose:
+Let $\mathcal{R}=\{(s^1,s^2|\Pred_{s^1,s^2})\}$ be a relation over the set $\mathcal{S}_1$ and $\mathcal{S}_2$ constrained by a predicate: if $(s^1,s^2) \in \mathcal{R}$ then $\Pred_{s^1,s^2}$ is  true.}
+
+ FH-bisimulation is defined formally: 
  \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim}
@@
    and of the same sort.  %\LUDO{changed:} 
-      Let 
-      \ERIC{$\mathcal{R}=\{(s^1,s^2|\Pred_{s^1,s^2})\}$} be a
-      relation over the sets 
-      $\mathcal{S}_1$ and $\mathcal{S}_2$ 
-      constrained by a predicate.  More precisely, for any pair $(s^1,s^2)$, there is a 
-      single
-      $(s^1,s^2|\Pred_{s^1,s^2})\in\mathcal{R}$  stating that $s^1$ and $s^2$ are related if $\Pred_{s^1,s^2}$\ 
-      is 
-      true.
 \end{minipage}
@@
        	Let $\mathcal{R}''$ be the relation: 
-       	\[\mathcal{R}'' = \{(s^1,s^3|\Pred\,'')|\,\Pred\,''=\bigvee_{ \begin{array}{l}
+       	\[\mathcal{R}'' = \{(s^1,s^3|\Pred\,'')\,\,\Big|\,\Pred\,''=\bigvee_{\begin{array}{c}       		
        		(s^1,s^2|\Pred)\in\mathcal{R}\\ (s^2,s^3|\Pred\,')\in\mathcal{R}' 	
@@
 This relation is the adaptation of the transitivity to the conditional relationship that 
-defines a bisimulation. Indeed the global disjunction together with the conjuction of 
+defines a bisimulation. Indeed the global disjunction together with the conjunction of 
 predicates plays exactly the role of the intermediate element in a transitivity rule: 

### 2017-10-04 2016-Weak-FH-Bisim/WeakBisim.tex
notations

@@
 methods of different interfaces).
-We denote $y\gets x$ a substitution. Application of the substitution is denoted
+We denote $y\gets x$ a substitution. The application of the substitution is denoted
 $\subst{y\gets x}$, the operation replaces in a term all occurrences 
@@
 
-\RAB{Exemple a revoir. Les regles ne passent...}
+\RAB{Exemple  Fig3 a revoir: Les regles ne passent... }
 
@@
 \emph{internal actions} depending on a specific action
-algebra. Naturely, an internal action cannot be synchronised with
+algebra. Naturally, an internal action cannot be synchronised with
 actions of other systems in its environment.
@@
 
-Classicaly, we start by defining a derived transition relation based
+Classically, we start by defining a derived transition relation based
 on sequences of invisible actions:
@@
 
-Two pNets are Weak FH-bisimilar if there exist a relation between their associated 
-automata that is an Weak FH-bisimulation and their initial sstates are equivalent.
+Two pNets are Weak FH-bisimilar if there exist a relation between their associated open
+automata that is an Weak FH-bisimulation and their initial states are equivalent.
 

### 2017-10-16 2016-Weak-FH-Bisim/WeakBisim.tex
Solved some comments

@@
 family is denoted $\emptyset$. We
-denote classically $\overline{a}$ a family when the indexing set is
+denote classically with an overline -- $\overline{a}$  -- a family when the indexing set 
+is
 not meaningful.  $\uplus$ is the disjoint union on
@@
 
-\RAB{La notation overline n'a pas ete introduite auparavant? Aussi, je n'ai pas trop bien saisi quand on utilise overline et la la notation k in K}
+\RAB{La notation overline n'a pas ete introduite auparavant? Aussi, je n'ai pas trop bien 
+saisi quand on utilise overline et la la notation k in K}\LUDO{DONE}
 
@@
 
-\TODO{say that This predicate entails a verification of satisfiability}
+Somehow, this predicate entails a verification of satisfiability in the sense that if the 
+predicate $\Pred_{\symb{sv}}$ is not satisfiable, then the transition associated with the 
+synchronisation will not occur in the considered state.
 
@@
    single
-      $(s^1,s^2|\Pred_{s^1,s^2})\in\mathcal{R}$  stating that $s^1$ and $s^2$ are related if $\Pred_{s^1,s^2}$\ 
+      $(s^1,s^2|\Pred_{s^1,s^2})\in\mathcal{R}$  stating that $s^1$ and $s^2$ are related 
+      if $\Pred_{s^1,s^2}$ 
       is 
-      true.
+      true, i.e. the states are related when the variables in $s^1$ and $s^2$ verify the 
+      predicate $\Pred_{s^1,s^2}$.
 
 \RAB{ I propose:
-Let $\mathcal{R}=\{(s^1,s^2|\Pred_{s^1,s^2})\}$ be a relation over the set $\mathcal{S}_1$ and $\mathcal{S}_2$ constrained by a predicate: if $(s^1,s^2) \in \mathcal{R}$ then $\Pred_{s^1,s^2}$ is  true.}
+Let $\mathcal{R}=\{(s^1,s^2|\Pred_{s^1,s^2})\}$ be a relation over the set 
+$\mathcal{S}_1$ and $\mathcal{S}_2$ constrained by a predicate: if $(s^1,s^2) \in 
+\mathcal{R}$ then $\Pred_{s^1,s^2}$ is  true.}  \LUDO{No : this is not the meaning}
 
@@
    and of the same sort.  %\LUDO{changed:}
+
+ Then 
+$\mathcal{R}$ is an FH-bisimulation iff for any  states
+$s^1\in\mathcal{S}_1$ and $s^2\in\mathcal{S}_2$, $(s^1,s^2|\Pred)\in\mathcal{R}$, we 
+have
+the following:
 \end{minipage}
@@
 \end{minipage}
- Then 
-   $\mathcal{R}$ is an FH-bisimulation iff for any  states
-   $s^1\in\mathcal{S}_1$ and\\ $s^2\in\mathcal{S}_2$, $(s^1,s^2|\Pred)\in\mathcal{R}$, we 
-   have
-   the following:
 

### 2017-10-17 2016-Weak-FH-Bisim/WeakBisim.tex
Small changes during the meeting

@@
  transitions, but also as a reference to the work of De Simone~\cite{deSimone85},
- that pioneered this idea.\\
-\TODO{To check:}
+ that pioneered this idea.
+
 Let \ERIC{$\mathcal{R}=\{(s^1,s^2|\Pred_{s^1,s^2})\}$} be a relation over the set $\mathcal{S}_1$ and $\mathcal{S}_2$ constrained by a predicate
@@
       predicate $\Pred_{s^1,s^2}$.
-
-\RAB{ I propose:
-Let $\mathcal{R}=\{(s^1,s^2|\Pred_{s^1,s^2})\}$ be a relation over the set 
-$\mathcal{S}_1$ and $\mathcal{S}_2$ constrained by a predicate: if $(s^1,s^2) \in 
-\mathcal{R}$ then $\Pred_{s^1,s^2}$ is  true.}  \LUDO{No : this is not the meaning}
 
@@
        	of 
-       	$\mathcal{T}_2$ and of  $\mathcal{T}_3$; members of $\mathcal{R}2$ are of the 
+       	$\mathcal{T}_2$ and of  $\mathcal{T}_3$; members of $\mathcal{R}'$ are of the 
        	form 
@@
 conjunction of states expresses the intermediate predicate is used to ensure 
-satisfiability of the predicate relating the first state to the last one..
+satisfiability of the predicate relating the first state to the last one.
 
@@
        	For any $p\in P$ by definition of $\mathcal{R}''$,
-       	$(s^1,s^2_p|\Pred_p)\in\mathcal{R}$,  and $(s^2_p,s^3|\Pred\,'_p)\in\mathcal{R}$. 
+       	$(s^1,s^2_p|\Pred_p)\in\mathcal{R}$,  and 
+       	$(s^2_p,s^3|\Pred\,'_p)\in\mathcal{R}'$. 
        	We have 
@@
        	following by definition of bisimulation.
-       	For any open transition $OT$ in $\mathcal{T}_1$ originating from $s^1$:
+       	For any open transition $OT$ in $\mathcal{T}_1$ originating from $s^1$.
        	Additionally we have $\Pred\,'' = \bigvee_{p\in P} \Pred_p\land\Pred_p\,'$.
@@
 
-       	there exist open transitions $OT_{p x}^{x\in X} \subseteq \mathcal{T}_2$:
+       	There exist open transitions $OT_{p x}^{x\in X} \subseteq \mathcal{T}_2$:
 
@@
        	$(s^2_p,s^3|\Pred\,^\prime_p)\in\mathcal{R}'$ there exist open transitions
-       	$OT_{pxy}^{x\in X, y\in Y} \subseteq \mathcal{T}_3$:
+       	$OT_{pxy}^{y\in Y} \subseteq \mathcal{T}_3$:
 
@@
        	(s^{2}_x,s^{3}_{pxy}|\Pred_{target_{pxy}})\in \mathcal{R}'$; and  \\
-       	$\Pred\,'_p \land \Pred_{OT_x}\\
+       	$\Pred\,'_p \land \Pred_{OT_{p x}}\\
        	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}

### 2017-11-14 2016-Weak-FH-Bisim/WeakBisim.tex
Cleaned up sorts

@@
 \usepackage{graphicx}
+\usepackage{DotArrow}
 
@@
 A pNet is a hierarchical structure where leaves are pLTSs and holes:\\
-$\pNet\triangleq pLTS~|~\mylangle \pNet_i^{i\in I}, Sort_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle$
+$\pNet\triangleq pLTS~|~\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in 
+K}\myrangle$
 where
@@
 $I$ and $J$ are \emph{disjoint}: $I\!\cap\! J=\emptyset$,  $I\!\cup\! J\neq\emptyset$
-\item[$\bullet$] $Sort_j \subseteq \AlgAS$ is a set of action terms, denoting the $\Sort$ of
+\item[$\bullet$] $\Sort_j \subseteq \AlgAS$ is a set of action terms, denoting the 
+\emph{sort} of
 hole $j$.
@@
   I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$,  $\forall j\!\in\!
-  J_k.\,\alpha_{j}\!\in\!Sort_j$, and $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
+  J_k.\,\alpha_{j}\!\in\!\Sort_j$, and $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
   J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
@@
 \begin{array}{l}
-\Sort(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{x \gets ?x| 
+\Sortop(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{x \gets ?x| 
 x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
     J}\rangle} s'\in \to \} \\
-\Sort(\mylangle \pNet_i^{i\in I}\!,Sort_j^{j\in J}\!,
+\Sortop(\mylangle \overline{\pNet}\!, %\pNet_i^{i\in I}, \Sort_j^{j\in J}
+\overline{\pNet}\!,
 \overline{\symb{SV}}\myrangle)
-=\{\alpha'_k |\, \alpha_j^{j\in J_k}\to\alpha'_k\in\set{\symb{SV}}\}
+=\{\alpha' |\, \overline{\alpha}%\alpha_j^{j\in J_k}
+\to\alpha'\in\set{\symb{SV}}\}
 \end{array}
@@
 \Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset \\
-\Holes(\mylangle \pNet_i^{i\in I}\!,Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) =J\cup{\displaystyle \bigcup_{i\in I}\Holes(\pNet_i)}\\
+\Holes(\mylangle \pNet_i^{i\in I}\!,\Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) 
+=J\cup{\displaystyle \bigcup_{i\in 
+I}\Holes(\pNet_i)}\\
 \forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
@@
 \Leaves(\mylangle S,s_0, \to\myrangle) \!=\! \{ \mylangle S,s_0, \to\myrangle \}\\
-\Leaves(\mylangle \pNet_i^{i\in I}\!,Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \bigcup_{i\in I}\Leaves(\pNet_i)}
+\Leaves(\mylangle \pNet_i^{i\in I}\!,%Sort_j^{j\in J}
+\overline{\Sort}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \bigcup_{i\in 
+I}\Leaves(\pNet_i)}
 \end{array}\]
@@
 	I}$ of LTSs, a
-	set $J$ of holes with sorts $Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is a structure of the form:	
+	set $J$ of holes with sorts $\Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is 
+	a structure of the form:	
 	\begin{mathpar}
@@
         is a transition of the hole $j$, for any action $b_j$ in the
-        sort $Sort_j$. $v$ is a variable denoting the resulting action
+        sort $\Sort_j$. $v$ is a variable denoting the resulting action
         of this open transition. \Pred\ is a predicate 
@@
 Let
-$\mylangle\overline{\pNet},\overline{Sort},\symb{SV}_k^{k\in K} \myrangle$
+$\mylangle\overline{\pNet},\overline{\Sort},\symb{SV}_k^{k\in K} \myrangle$
 be a pNet. Consider a synchronisation vector $SV_k$, for $k\in K$. We define a
@@
     }
-    {\mylangle \pNet_i^{i\in I}, Sort_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle
+    {\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle
     	\models
@@
 \begin{definition}[pNet composition]
-	An open pNet: $\pNet = \mylangle \pNet_i^{i\in I}, Sort_j^{j\in J}, 
+	An open pNet: $\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
 	\overline{\symb{SV}}\myrangle$
@@
 	\[\pNet\left[\pNet'\right]_{j_0}= \mylangle 
-	\pNet_i^{i\in I}\uplus\{j_0\mapsto \pNet'\},Sort_j^{j\in J\setminus \{j_0\}},
+	\pNet_i^{i\in I}\uplus\{j_0\mapsto \pNet'\},\Sort_j^{j\in J\setminus \{j_0\}},
 	\overline{\symb{SV}}\myrangle
@@
 	Consider an open pNet:
-	$\pNet = \mylangle \pNet_i^{i\in I}, Sort_j^{j\in J}, 
+	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
 	\overline{\symb{SV}}\myrangle$.
 	Let $j_0\in J$ be a hole. Let $Q$ and $Q'$ be two FH-bisimilar pNets such that 
-	$\Sort(Q)=\Sort(Q')=Sort_{j_0}$\footnote{Note that $\Sort(Q)=\Sort(Q')$ is ensured by 
+	$\Sortop(Q)=\Sortop(Q')=\Sort_{j_0}$\footnote{Note that $\Sortop(Q)=\Sortop(Q')$ is 
+	ensured by 
 	strong bisimilarity.}. Then 
@@
 	Consider two FH-bisimilar open pNets:
-	$\pNet = \mylangle \pNet_i^{i\in I}, Sort_j^{j\in J}, 
+	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
 	\overline{\symb{SV}}\myrangle$ and 	$\pNet' = \mylangle {\pNet'}_i^{i\in I}, 
-	Sort_j^{j\in 
+	\Sort_j^{j\in 
 	J}, 	\overline{\symb{SV'}}\myrangle$ 
 	(recall they must have the same holes to be bisimilar).
-	Let $j_0\in J$ be a hole, and $Q$ be a pNet such that $\Sort(Q)=Sort_{j_0}$. Then $\pNet[Q]_{j_0}$ and 
+	Let $j_0\in J$ be a hole, and $Q$ be a pNet such that $\Sortop(Q)=\Sort_{j_0}$. Then 
+	$\pNet[Q]_{j_0}$ and 
 	$\pNet'[Q]_{j_0}$ are FH-bisimilar.
@@
 	$\Pred_{Root} = ( a \!=\! ium(?tgt2_2) \land b\!=\!um(t2) \land b\in
-	Sort_{P21} \land t2 = tgt2_2
+	\Sort_{P21} \land t2 = tgt2_2
 	\land v \!= \! \underline{um(t2)} )  $
@@
 
-$Pred_{UM\_21} =  [um(t1)=b \land b\in Sort_{P21} \land um(t1)=v_{SG2}]$
+$Pred_{UM\_21} =  [um(t1)=b \land b\in \Sort_{P21} \land um(t1)=v_{SG2}]$
 
@@
 %% $Pred_{Root} = [ium(?t2) = ium(t2) \land b=um(t1) \land
-%%   b\in Sort_{P21} \land v_{SG2}=um(t1) \land v_{SG2} = um(t2)
+%%   b\in \Sort_{P21} \land v_{SG2}=um(t1) \land v_{SG2} = um(t2)
 %%   \land v = \tau]  $
@@
 That can be simplified (eliminating the vector local variables and the
-intermediate resulting actions), as: $Pred1 = [b\in Sort_{P21}
+intermediate resulting actions), as: $Pred1 = [b\in \Sort_{P21}
   \land b=um(tgt2_2) \land v=\underline{b} ]  $
@@
 $Pred_{Root} = [tgt1_1=tgt2_2 \land b=um(tgt2_2) \land
-  b\in Sort_{P3} \land v = \underline{bm(tgt2_2)}]  $
+  b\in \Sort_{P3} \land v = \underline{bm(tgt2_2)}]  $
 
@@
 
-$Pred_{HB\_2} = [im(tgt1_1) = im(t3) \land bm(tgt2_2) = bm(t3) \land b= im(t3) \land b\in Sort_{P3}  \land v = \underline{bm(t3)}]$
+$Pred_{HB\_2} = [im(tgt1_1) = im(t3) \land bm(tgt2_2) = bm(t3) \land b= im(t3) \land b\in 
+\Sort_{P3}  \land v = \underline{bm(t3)}]$
 
@@
 $Pred2 = [tgt1_1=tgt2_2 \land
-  b\in Sort_{P3} \land b=um(tgt2_2) \land v = \underline{bm(tgt2_2)}]
+  b\in \Sort_{P3} \land b=um(tgt2_2) \land v = \underline{bm(tgt2_2)}]
 $
@@
          {\ostate{000} \xrightarrow{um(tgt2_2)} \ostate{020}}\\
- with & P1 = [b1\in Sort_{P21} \land b1=um(tgt2_2) ]
+ with & P1 = [b1\in \Sort_{P21} \land b1=um(tgt2_2) ]
  \\
@@
          with & P2 = [tgt1_1=tgt2_2 \land IsDirectRelative(2,tgt2_2)
-           \land  b2\in Sort_{P3} \land b2=um(tgt2_2) ]
+           \land  b2\in \Sort_{P3} \land b2=um(tgt2_2) ]
          \\
@@
          with & P3 = [tgt11_1=tgt1_1 \land IsAncestor(1,tgt1_1)
-           \land  b3\in Sort_{P12} \land b3=im(tgt1_1) ]
+           \land  b3\in \Sort_{P12} \land b3=im(tgt1_1) ]
          \\
@@
          {\ostate{001} \xrightarrow{\underline{dm(tgt11)}} \ostate{000}}\\
- with & P4 = [ b4=im(tgt11_1) \land  b4\in Sort_{P111} \land IsAncestor(11,tgt11_1) ]
+ with & P4 = [ b4=im(tgt11_1) \land  b4\in \Sort_{P111} \land IsAncestor(11,tgt11_1) ]
          \\
@@
          {\ostate{000} \xrightarrow{im(?a)} \ostate{110}}\\
- with & P7 = [ tgt1_1 = tgt2_1 = a \land b7\in Sort_{P3} \land b7 = im(?a)  ]
+ with & P7 = [ tgt1_1 = tgt2_1 = a \land b7\in \Sort_{P3} \land b7 = im(?a)  ]
  \\
@@
    \begin{itemize}
-   \item Unicast: $\Sort (gw_{\widetilde{g}})=\{?m_{\widetilde{g}}(\widetilde{tgt}), !um_{\widetilde{g}}(\widetilde{tgt}),!dm_{\widetilde{g}}(\widetilde{tgt}), ERROR_{g}\}$
-   \item Flat Broadcast: $\Sort (gw_{\widetilde{g}})=\{?m_{\widetilde{g}}(\widetilde{tgt}), !um_{\widetilde{g}}(\widetilde{tgt}),!dm_{\widetilde{g}}(\widetilde{tgt}), ?um_{\widetilde{g}}(\widetilde{tgt})\}$
-   \item Hierarchical Broadcast: $\Sort (gw_{\widetilde{g}})=\{?m_{\widetilde{g}}(\widetilde{tgt}), ?um_{\widetilde{g}}(\widetilde{tgt}), !um_{\widetilde{g}}(\widetilde{tgt}),!dm_{\widetilde{g}}(\widetilde{tgt}), !bm_{\widetilde{g}}(\widetilde{tgt}),DISCARD,
+   \item Unicast: $\Sortop (gw_{\widetilde{g}})=\{?m_{\widetilde{g}}(\widetilde{tgt}), 
+   !um_{\widetilde{g}}(\widetilde{tgt}),!dm_{\widetilde{g}}(\widetilde{tgt}), ERROR_{g}\}$
+   \item Flat Broadcast: $\Sortop 
+   (gw_{\widetilde{g}})=\{?m_{\widetilde{g}}(\widetilde{tgt}), 
+   !um_{\widetilde{g}}(\widetilde{tgt}),!dm_{\widetilde{g}}(\widetilde{tgt}), 
+   ?um_{\widetilde{g}}(\widetilde{tgt})\}$
+   \item Hierarchical Broadcast: $\Sortop 
+   (gw_{\widetilde{g}})=\{?m_{\widetilde{g}}(\widetilde{tgt}), 
+   ?um_{\widetilde{g}}(\widetilde{tgt}), 
+   !um_{\widetilde{g}}(\widetilde{tgt}),!dm_{\widetilde{g}}(\widetilde{tgt}), 
+   !bm_{\widetilde{g}}(\widetilde{tgt}),DISCARD,
        ERROR_{g}\}$
@@
 \begin{itemize}
-\item Unicast: $\Sort(pc_{\widetilde{p}})=\{!m_{\widetilde{p}}(\widetilde{tgt}),
+\item Unicast: $\Sortop(pc_{\widetilde{p}})=\{!m_{\widetilde{p}}(\widetilde{tgt}),
 ?m_{\widetilde{p}}(\widetilde{tgt})\}$
-\item Flat Broadcast: $\Sort(pc_{\widetilde{p}})=\{!m_{\widetilde{p}},
+\item Flat Broadcast: $\Sortop(pc_{\widetilde{p}})=\{!m_{\widetilde{p}},
 ?m_{\widetilde{p}}\}$
@@
 
-\item[$\bullet$] The subgroup $sg_{\widetilde{g}}$ can be taken the hole of open pNets which can be inserted the sub-pNets(subgroups) and has the sort: $\Sort (sg_{\widetilde{g}})=\{?m_{\widetilde{g}}(\widetilde{t}), !m_{\widetilde{g}}(\widetilde{t})\}$;
+\item[$\bullet$] The subgroup $sg_{\widetilde{g}}$ can be taken the hole of open pNets 
+which can be inserted the sub-pNets(subgroups) and has the sort: $\Sortop 
+(sg_{\widetilde{g}})=\{?m_{\widetilde{g}}(\widetilde{t}), 
+!m_{\widetilde{g}}(\widetilde{t})\}$;
 

### 2017-11-14 2016-Weak-FH-Bisim/WeakBisim.tex
New OT arrows

@@
 		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred, \Post}
-	{s \xrightarrow {v}s'}
+	{s \OTarrow {v}s'}
 	\end{mathpar}
@@
   %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
-    {A1_0 \xrightarrow{\underline{\delta(x4)}} A1_1}
+    {A1_0 \OTarrow{\underline{\delta(x4)}} A1_1}
   $
@@
 			e_b,\left\{x_j\gets e_j\right\}^{j\in J}}
-			{\ostate{s} \xrightarrow{\alpha} \ostate{s'}}
+			{\ostate{s} \OTarrow{\alpha} \ostate{s'}}
 		}
@@
     	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
-    	{\ostate{s_{i}^{i \in L_m}} \xrightarrow {v_m}
+    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
     		\ostate{(s_i^\prime)^{i\in L_m}}}
@@
     		\Post_m}
-    		{\ostate{s_i^{i\in L}} \xrightarrow {v}
+    		{\ostate{s_i^{i\in L}} \OTarrow {v}
     			\ostate{(s_i^\prime)^{i\in L}}}
@@
               v_1=\delta(x_1)}
-                      {\ostate{0}\xrightarrow{v_1}\ostate{1}}
+                      {\ostate{0}\OTarrow{v_1}\ostate{1}}
         }\\
@@
                       \sm{Pred}_{C_4}}
-                      {\ostate{0}\xrightarrow{l}\ostate{0}}
+                      {\ostate{0}\OTarrow{l}\ostate{0}}
               }
@@
                   }
-                  {\ostate{0}\xrightarrow{v_2}\ostate{0}}
+                  {\ostate{0}\OTarrow{v_2}\ostate{0}}
         }   
@@
            }
-         {\ostate{00} \xrightarrow{v} \ostate{10}}
+         {\ostate{00} \OTarrow{v} \ostate{10}}
       }\vspace{-4ex}
@@
            \{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
-         {s^1 \xrightarrow {v} s^{1'}}
+         {s^1 \OTarrow {v} s^{1'}}
 
@@
            \{\xrightarrow{b_{j x}}_j\}^{j\in J_{2x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {s^2 \xrightarrow {v_x} s^{2}_x}
+         {s^2 \OTarrow {v_x} s^{2}_x}
 %         \right)
@@
            \{\xrightarrow{b_j}_j\}^{j\in J},\Pred,\Post}
-         {s \xRightarrow {v} s'}
+         {s \OTWeakarrow {v} s'}
          \in \mathcal{T}^*
@@
            \{\xrightarrow{b_{j x}}_j\}^{j\in J_{2x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {s^2 \xRightarrow {v_x} s^{2'}_x}
+         {s^2 \OTWeakarrow {v_x} s^{2'}_x}
 \end{mathpar}
@@
     	\\\xrightarrow{a1}_P\\ a1\neq\delta(x)}
-    {\ostate{00} \xrightarrow{a1} \ostate{00}}\\
+    {\ostate{00} \OTarrow{a1} \ostate{00}}\\
     OT_2 & = \openrule{
@@
                       }
-                      {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}    \\
+                      {\ostate{00} \OTarrow{\underline{\delta(x1)}} \ostate{10}}    \\
     OT_3 & = \openrule{0 \xrightarrow{l}_{C_4} 0,
@@
                         }
-    {\ostate{10} \xrightarrow{a2} \ostate{10}}\\
+    {\ostate{10} \OTarrow{a2} \ostate{10}}\\
     OT_4 & = \openrule{
@@
                        }
-                      {\ostate{10} \xrightarrow{\underline{\delta(x2)}} \ostate{11}}    \\
+                      {\ostate{10} \OTarrow{\underline{\delta(x2)}} \ostate{11}}    \\
     OT_5 & = \openrule{1 \xrightarrow{r}_{C_3} 1, \\1 \xrightarrow{r}_{C_4} 1, 
@@
     	}
-    {\ostate{11} \xrightarrow{a3} \ostate{11}}
+    {\ostate{11} \OTarrow{a3} \ostate{11}}
     \end{eqnarray*}
@@
                }
-             {\ostate{00} \xrightarrow{b1} \ostate{00}}\\
+             {\ostate{00} \OTarrow{b1} \ostate{00}}\\
     OT'_2 & = \openrule
@@
                       }
-             {\ostate{00} \xrightarrow{\underline{\delta(y1)}} \ostate{01}}\\
+             {\ostate{00} \OTarrow{\underline{\delta(y1)}} \ostate{01}}\\
     OT'_3 & = \openrule
@@
                }
-    {\ostate{01} \xrightarrow{b2} \ostate{01}}\\
+    {\ostate{01} \OTarrow{b2} \ostate{01}}\\
     OT'_4 & = \openrule
@@
                                  }
-             {\ostate{01} \xrightarrow{\underline{\delta(y2)}} \ostate{11}}    \\
+             {\ostate{01} \OTarrow{\underline{\delta(y2)}} \ostate{11}}    \\
     OT'_5 & = \openrule
@@
              	}
-             {\ostate{11} \xrightarrow{b3} \ostate{11}}
+             {\ostate{11} \OTarrow{b3} \ostate{11}}
     \end{eqnarray*}
@@
        		\{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
-       	{s^1 \xrightarrow {v} {s^{1}}'}
+       	{s^1 \OTarrow {v} {s^{1}}'}
 
@@
        		\{\xrightarrow{b_{j p x}}_j\}^{j\in J_{2px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
-       	{s^2_p \xrightarrow {v_{px}} s^{2}_{px}}
+       	{s^2_p \OTarrow {v_{px}} s^{2}_{px}}
        	%         \right)
@@
        		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
-       	{s^3 \xrightarrow {v_{pxy}} s^{3}_{pxy}}
+       	{s^3 \OTarrow {v_{pxy}} s^{3}_{pxy}}
        	%         \right)
@@
 				\Post}
-			{\ostate{s_i^{i\in L}} \xrightarrow {v}
+			{\ostate{s_i^{i\in L}} \OTarrow {v}
 				\ostate{s_i^{\prime i\in L}}}
@@
 				\Post'}
-			{\ostate{s_i^{i\in L\setminus L_Q}} \xrightarrow {v}
+			{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {v}
 				\ostate{s_i'^{\, i\in L\setminus L_Q}}}
@@
 				\Post''}
-			{\ostate{s_i^{i\in L_Q}} \xrightarrow {v_Q}
+			{\ostate{s_i^{i\in L_Q}} \OTarrow {v_Q}
 				\ostate{s_i'^{\, i\in L_Q}}}
@@
 	\{\xrightarrow{b_{j}}_j\}^{j\in J_m}, \Pred_m, \Post_m}
-{\ostate{s_{i}^{i \in L_m}} \xrightarrow {v_m}
+{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
 	\ostate{s_{i}^{\prime\ i \in L_m}}}\]
@@
 			\Post''}
-		{\ostate{s_i^{i\in L_Q}} \xrightarrow {v_{j_0}}
+		{\ostate{s_i^{i\in L_Q}} \OTarrow {v_{j_0}}
 			\ostate{s_i'^{\, i\in L_Q}}}
@@
 		\Post}
-	{\ostate{s_i^{i\in L}} \xrightarrow {v}
+	{\ostate{s_i^{i\in L}} \OTarrow {v}
 		\ostate{s_i'^{\, i\in L}}}
@@
 		\Post'}
-	{\ostate{s_i^{i\in L_Q}} \xrightarrow {v_Q}
+	{\ostate{s_i^{i\in L_Q}} \OTarrow {v_Q}
 		\ostate{s_i'^{\, i\in L_Q}}}
@@
 			\Post\uplus \Post'}
-		{\ostate{s_i^{i\in L\uplus L_Q}} \xrightarrow {v}
+		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {v}
 			\ostate{s_i^{\prime i\in L\uplus L_Q}}}
@@
 	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
-{\ostate{s_{i}^{i \in L_k}} \xrightarrow {v_m}
+{\ostate{s_{i}^{i \in L_k}} \OTarrow {v_m}
 	\ostate{s_{i}^{\prime\ i \in L_k}}}\]
@@
  	\{\xrightarrow{b_j}_j\}^{j\in J},\Pred_{OT},\Post_{OT}}
- { \ostate{s_{1 i}^{i \in L_P\uplus L}}\xrightarrow {v} \ostate{{s'}_{1 i}^{i \in 
+ { \ostate{s_{1 i}^{i \in L_P\uplus L}}\OTarrow {v} \ostate{{s'}_{1 i}^{i \in 
  			L_P\uplus 
@@
  		\Post'}
- 	{\ostate{s_{1 i}^{i\in L_P}} \xrightarrow {v}
+ 	{\ostate{s_{1 i}^{i\in L_P}} \OTarrow {v}
  		\ostate{s_{1 i}'^{\, i\in L_P}}}
@@
  		\Post''}
- 	{\ostate{s_{1 i}^{i\in L}} \xrightarrow {v_Q}
+ 	{\ostate{s_{1 i}^{i\in L}} \OTarrow {v_Q}
  		\ostate{s_{1 i}'^{\, i\in L}}}
@@
  	\Pred_{OT_x},\Post_{OT_x}}
- {\ostate{s_{2 i}^{i\in L'}} \xrightarrow {v_x} \ostate{s_{2 i x}^{i\in L'}}}
+ {\ostate{s_{2 i}^{i\in L'}} \OTarrow {v_x} \ostate{s_{2 i x}^{i\in L'}}}
  \end{mathpar}
@@
  		\Post'\uplus \Post_{OT_x} }
- 	{\ostate{s_{2 i }^{i\in L'\uplus L_Q}} \xrightarrow {v_x}
+ 	{\ostate{s_{2 i }^{i\in L'\uplus L_Q}} \OTarrow {v_x}
  		\ostate{{s}_{2 i x}^{i\in L'\uplus L_Q}}}
@@
 		\{\xrightarrow{b_j}_j\}^{j\in J},\Pred_{OT},\Post_{OT}}
-	{ \ostate{s_{1 i}^{i \in L\uplus L_Q}}\xrightarrow {v} \ostate{{s'}_{1 i}^{i \in 
+	{ \ostate{s_{1 i}^{i \in L\uplus L_Q}}\OTarrow {v} \ostate{{s'}_{1 i}^{i \in 
 	L\uplus 
@@
 					\Post'}
-				{\ostate{s_{1 i}^{i\in L}} \xrightarrow {v}
+				{\ostate{s_{1 i}^{i\in L}} \OTarrow {v}
 					\ostate{s_{1 i}'^{\, i\in L}}}
@@
 					\Post''}
-				{\ostate{s_{1 i}^{i\in L_Q}} \xrightarrow {v_Q}
+				{\ostate{s_{1 i}^{i\in L_Q}} \OTarrow {v_Q}
 					\ostate{s_{1 i}'^{\, i\in L_Q}}}
@@
 				\Pred_{OT_x},\Post_{OT_x}}
-			{\ostate{s_{2 i}^{i\in L'}} \xrightarrow {v_x} \ostate{s_{2 i x}^{i\in L'}}}
+			{\ostate{s_{2 i}^{i\in L'}} \OTarrow {v_x} \ostate{s_{2 i x}^{i\in L'}}}
 			%         \right)
@@
 						\Post_{OT_x}\uplus \Post''}
-					{\ostate{s_{2 i }^{i\in L'\uplus L_Q}} \xrightarrow {v_x}
+					{\ostate{s_{2 i }^{i\in L'\uplus L_Q}} \OTarrow {v_x}
 						\ostate{{s}_{2 i x}^{i\in L'\uplus L_Q}}}
@@
 			\\ \sm{Pred}_{Root} \\ \emptyset}
-		{\ostate{000} \xrightarrow{v} \ostate{020}}
+		{\ostate{000} \OTarrow{v} \ostate{020}}
 		$
@@
           \\ \sm{Pred1}}
-         {\ostate{000} \xrightarrow{v} \ostate{020}}
+         {\ostate{000} \OTarrow{v} \ostate{020}}
       }      ~~ [UG\_2]
@@
            \quad Pred_{Root}}
-         {\ostate{020} \xrightarrow{v} \ostate{100}}
+         {\ostate{020} \OTarrow{v} \ostate{100}}
 \end{mathpar}
@@
               {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad \sm{True}}
-              {\ostate{0} \xrightarrow{im(?tgt1_1)} \ostate{1}}
+              {\ostate{0} \OTarrow{im(?tgt1_1)} \ostate{1}}
         }
@@
                  {2 \xrightarrow{bm(tgt2_2)}_{gw2} 0 \quad \sm{Pred}_{gw2}}
-                 {\ostate{2} \xrightarrow{bm(tgt2_2)} \ostate{0}}
+                 {\ostate{2} \OTarrow{bm(tgt2_2)} \ostate{0}}
            }
@@
            \quad Pred2}
-         {\ostate{020} \xrightarrow{v} \ostate{100}}}
+         {\ostate{020} \OTarrow{v} \ostate{100}}}
       ~~ [HB\_2]
@@
           \quad P1}
-         {\ostate{000} \xrightarrow{um(tgt2_2)} \ostate{020}}\\
+         {\ostate{000} \OTarrow{um(tgt2_2)} \ostate{020}}\\
  with & P1 = [b1\in \Sort_{P21} \land b1=um(tgt2_2) ]
@@
            \quad P2}
-         {\ostate{020} \xrightarrow{\underline{bm(tgt2_2)}} \ostate{100}}\\
+         {\ostate{020} \OTarrow{\underline{bm(tgt2_2)}} \ostate{100}}\\
          with & P2 = [tgt1_1=tgt2_2 \land IsDirectRelative(2,tgt2_2)
@@
            \quad P3}
-         {\ostate{100} \xrightarrow{\underline{dm(tgt1_1)}} \ostate{001}}\\
+         {\ostate{100} \OTarrow{\underline{dm(tgt1_1)}} \ostate{001}}\\
          with & P3 = [tgt11_1=tgt1_1 \land IsAncestor(1,tgt1_1)
@@
            \quad P4}
-         {\ostate{001} \xrightarrow{\underline{dm(tgt11)}} \ostate{000}}\\
+         {\ostate{001} \OTarrow{\underline{dm(tgt11)}} \ostate{000}}\\
  with & P4 = [ b4=im(tgt11_1) \land  b4\in \Sort_{P111} \land IsAncestor(11,tgt11_1) ]
@@
            \quad P5}
-         {\ostate{100} \xrightarrow{\underline{Discard}} \ostate{000}}\\
+         {\ostate{100} \OTarrow{\underline{Discard}} \ostate{000}}\\
  with & P5 = [IsDirectRelative(1,tgt1_1) ]
@@
            \quad P6}
-         {\ostate{020} \xrightarrow{\underline{Discard}} \ostate{000}}\\
+         {\ostate{020} \OTarrow{\underline{Discard}} \ostate{000}}\\
  with & P6 = [ IsAncestor(2,tgt2_2) ]
@@
            \quad P7}
-         {\ostate{000} \xrightarrow{im(?a)} \ostate{110}}\\
+         {\ostate{000} \OTarrow{im(?a)} \ostate{110}}\\
  with & P7 = [ tgt1_1 = tgt2_1 = a \land b7\in \Sort_{P3} \land b7 = im(?a)  ]
@@
            \quad P8}
-         {\ostate{110} \xrightarrow{Discard} \ostate{100}}\\
+         {\ostate{110} \OTarrow{Discard} \ostate{100}}\\
  with & P8 = [ IsDirectRelative(2,tgt2_1) ]

### 2017-11-14 2016-Weak-FH-Bisim/WeakBisim.tex
improved proof notations: s,t,u and removed target

@@
        	transitivity of the strong FH-bisimulation on states. Consider 3 open automata 
-       	$\mathcal{T}_1$, $\mathcal{T}_2$, $\mathcal{T}_3$ and states $s^1$, $s^2$, $s^3$ 
+       	$\mathcal{T}_1$, $\mathcal{T}_2$, $\mathcal{T}_3$ and states $s$, $t$, $u$ 
        	in those 
-       	automata\footnote{We omit the constraints stating that each $s^i_x$ is in the 
+       	automata\footnote{We omit the constraints stating that each $s_x,\,t_x,\,u_x$ is 
+       	in the 
        	states of 
-       		$\mathcal{T}_i$ for the sake of readability}.
+       		$\mathcal{T}_1,\,\mathcal{T}_2,\,\mathcal{T}_3$ for the sake of readability}.
        	Suppose we have $\mathcal{R}$ an FH-bisimulation relation between states of 
        	$\mathcal{T}_1$ and of  $\mathcal{T}_2$; members of $\mathcal{R}$ are of the form 
-       	$(s^1,s^2|\Pred)$.
+       	$(s,t|\Pred)$.
        	Suppose we also  have $\mathcal{R}'$ an FH-bisimulation relation between states 
@@
        	form 
-       	$(s^2,s^3|\Pred\,')$.
+       	$(t,u|\Pred\,')$.
 
        	Let $\mathcal{R}''$ be the relation: 
-       	\[\mathcal{R}'' = \{(s^1,s^3|\Pred\,'')\,\,\Big|\,\Pred\,''=\bigvee_{\begin{array}{c}       		
-       		(s^1,s^2|\Pred)\in\mathcal{R}\\ (s^2,s^3|\Pred\,')\in\mathcal{R}' 	
+       	\[\mathcal{R}'' = 
+       	\{(s,u|\Pred\,'')\,\,\Big|\,\Pred\,''=\bigvee_{\begin{array}{c}       		
+       		(s,t|\Pred)\in\mathcal{R}\\ (t,u|\Pred\,')\in\mathcal{R}' 	
        		\end{array}
@@
 
-       	The relation is built as follows: for each pair of state $s^1$, $s^3$, for each 
+       	The relation is built as follows: for each pair of state $s$, $u$, for each 
        	state 
-       	$s^2$ such that $\mathcal{R}$ relates $s^1$ and $s^2$, and $\mathcal{R}'$ relates 
-       	$s^2$ 
-       	and $s^3$, we take the conjunction of the two predicates. The predicates for 
+       	$t$ such that $\mathcal{R}$ relates $s$ and $t$, and $\mathcal{R}'$ relates 
+       	$t$ 
+       	and $u$, we take the conjunction of the two predicates. The predicates for 
        	different 
-       	values of $s^2$ are collected by a disjunction.
+       	values of $t$ are collected by a disjunction.
 
@@
        	that $\mathcal{R}''$ is an FH-bisimulation. Consider 
-       	$(s^1,s^3|\Pred\,'')\in\mathcal{R}''$. Then there is a set of states of 
-       	$\mathcal{T}_2$ relating $s^1$ and $s^3$, let $(s^2_p)^{p\in P}$ be this family.
+       	$(s,u|\Pred\,'')\in\mathcal{R}''$. Then there is a set of states of 
+       	$\mathcal{T}_2$ relating $s$ and $u$, let $(t_p)^{p\in P}$ be this family.
 
        	For any $p\in P$ by definition of $\mathcal{R}''$,
-       	$(s^1,s^2_p|\Pred_p)\in\mathcal{R}$,  and 
-       	$(s^2_p,s^3|\Pred\,'_p)\in\mathcal{R}'$. 
+       	$(s,t_p|\Pred_p)\in\mathcal{R}$,  and 
+       	$(t_p,u|\Pred\,'_p)\in\mathcal{R}'$. 
        	We have 
@@
        	following by definition of bisimulation.
-       	For any open transition $OT$ in $\mathcal{T}_1$ originating from $s^1$.
+       	For any open transition $OT$ in $\mathcal{T}_1$ originating from $s$.
        	Additionally we have $\Pred\,'' = \bigvee_{p\in P} \Pred_p\land\Pred_p\,'$.
@@
        	\inferrule*[myfraction=\reddottedrule]
-       	{\{s^1_i\xrightarrow{a_i}_i {s^{1}}'_i\}^{i\in I_1}, % , s^1_i,s^{1'}_i\in
+       	{\{s_i\xrightarrow{a_i}_i {s}'_i\}^{i\in I_1}, % , s^1_i,s^{1'}_i\in
        		%States(I_1)
        		\{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
-       	{s^1 \OTarrow {v} {s^{1}}'}
+       	{s \OTarrow {v} {s}'}
 
@@
        	\inferrule*[myfraction=\reddottedrule]
-       	{\{s^{2}_{pi}\xrightarrow{a_{p i x}}_i s^{2}_{p i x}\}^{i\in I_{2 p x}},
+       	{\{t_{p i}\xrightarrow{a_{p i x}}_i t_{p i x}\}^{i\in I_{2 p x}},
        		\{\xrightarrow{b_{j p x}}_j\}^{j\in J_{2px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
-       	{s^2_p \OTarrow {v_{px}} s^{2}_{px}}
+       	{t_p \OTarrow {v_{px}} t_{p x}}
        	%         \right)
@@
 
-       	such that  $\forall x, J_1=J_{2px}, (s^{1'},s^{2}_{px}|\Pred_{target_{px}})\in 
+       	such that  $\forall x, J_1=J_{2px}, (s',t_{px}|\Pred_{{px}})\in 
        	\mathcal{R}$;
@@
        	\land v\!=\!v_{px} \land
-       	\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)$
+       	\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)$
 
        	for any open transition $OT_{px}$, since
-       	$(s^2_p,s^3|\Pred\,^\prime_p)\in\mathcal{R}'$ there exist open transitions
+       	$(t_p,u|\Pred\,^\prime_p)\in\mathcal{R}'$ there exist open transitions
        	$OT_{pxy}^{y\in Y} \subseteq \mathcal{T}_3$:
@@
        	\inferrule*[myfraction=\reddottedrule]
-       	{\{s^{3}_i\xrightarrow{a_{i p x y}}_i s^{3}_{i p x y}\}^{i\in I_{3 p x y}},
+       	{\{u_i\xrightarrow{a_{i p x y}}_i u_{i p x y}\}^{i\in I_{3 p x y}},
        		\{\xrightarrow{b_{j p x y}}_j\}^{j\in J_{3pxy}}, 
        		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
-       	{s^3 \OTarrow {v_{pxy}} s^{3}_{pxy}}
+       	{u \OTarrow {v_{pxy}} u_{pxy}}
        	%         \right)
@@
        	such that  $\forall y, J_{2px}=J_{3pxy}, 
-       	(s^{2}_x,s^{3}_{pxy}|\Pred_{target_{pxy}})\in \mathcal{R}'$; and  \\
+       	(t_{px},u_{pxy}|\Pred_{{pxy}})\in \mathcal{R}'$; and  \\
        	$\Pred\,'_p \land \Pred_{OT_{p x}}\\
@@
        	\land v_{px}\!=\!v_{pxy} \land
-       	\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.
+       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.
 
@@
 
+       	First, $\forall y, \forall x, \forall p, J_1=J_{2px}=J_{3pxy}, 
+       	({s}',s_{pxy}|\Pred\,'_{{pxy}})\in \mathcal{R}''$. 
+       	Indeed for any 
+       	$p$, 
+       	$x$, and 
+       	$y$, $t_{px}$
+       	relate ${s}'$ and $u_{pxy}$, indeed
+       	$(s',t_{px}|\Pred_{{px}})\in \mathcal{R}$
+       	and $(t_{px},u_{pxy}|\Pred{{pxy}})\in \mathcal{R}'$. 
+       	More precisely, $t_{px} \in ({t_p}')^{p\in P'}$ where $({t_p}')^{p\in 
+       		P'}$ 
+       	is 
+       	the set of states relating ${s}'$ and $u_{pxy}$.
+       	Consequently, for all $p$, $x$, $y$, $\Pred_{px}\land 
+       	\Pred_{{pxy}}\implies 
+       	\Pred\,'_{{pxy}}$ (this is one element of the  disjunction defining the 
+       	predicate 
+       	relating ${s}'$ and $u_{pxy}$ in the definition of $\mathcal{R}''$).
+
 One can notice that, as bisimulation predicates are used to relate states that 
@@
 name clash. In practice,
-       	we can suppose that, as $\Pred\,'_{target_{pxy}}$ is used to relate states of 
+we can suppose that, as $\Pred\,'_{{pxy}}$ is used to relate states of 
 $\mathcal{T}_1$, and $\mathcal{T}_3$, there exists a predicate obtained by 
-       	renaming variables, that is equivalent to $\Pred\,'_{target_{pxy}}$ and does not 
+renaming variables, that is equivalent to $\Pred\,'_{{pxy}}$ and does not 
 contain the variables of 	$\mathcal{T}_2$. This predicate with ``fresh'' 
-       	variables is called   $\Pred\,'_{target_{pxy}}$ in the following.
-       	Similarly, we can suppose that $\Pred_{target_{px}}$ contains no 
-       	variable in $\mathcal{T}_3$, and $\Pred_{target_{pxy}}$ contains no 
+variables is called   $\Pred\,'_{{pxy}}$ in the following.
+Similarly, we can suppose that $\Pred_{{px}}$ contains no 
+variable in $\mathcal{T}_3$, and $\Pred_{{pxy}}$ contains no 
 variable in $\mathcal{T}_1$.
-
-       	First, $\forall y, \forall x, \forall p, J_1=J_{2px}=J_{3pxy}, 
-       	({s^{1}}',s^{3}_{pxy}|\Pred\,'_{target_{pxy}})\in \mathcal{R}''$. 
-       	Indeed for any 
-       	$p$, 
-       	$x$, and 
-       	$y$, $s^2_{px}$
-       	relate ${s^{1}}'$ and $s^{3}_{pxy}$, indeed
-       	$(s^{1'},s^{2}_{px}|\Pred_{target_{px}})\in \mathcal{R}$
-       	and $(s^{2}_x,s^{3}_{pxy}|\Pred_{target_{pxy}})\in \mathcal{R}'$. 
-       	More precisely, $s^{2}_{px} \in ({s^{2}_p}')^{p\in P'}$ where $({s^{2}_p}')^{p\in 
-       		P'}$ 
-       	is 
-       	the set of states relating ${s^{1}}'$ and $s^{3}_{pxy}$.
-       	Consequently, for all $p$, $x$, $y$, $\Pred_{target_{px}}\land 
-       	\Pred_{target_{pxy}}\implies 
-       	\Pred\,'_{target_{pxy}}$ (this is one element of the  disjunction defining the 
-       	predicate 
-       	relating ${s^{1}}'$ and $s^{3}_{pxy}$ in the definition of $\mathcal{R}''$).
 
@@
        		\land v\!=\!v_{pxy} \land
-       		\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
+       		\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
        	\end{small}
@@
        		\land v\!=\!v_{px} \land
-       		\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\land\Pred'_p\\
+       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\land\Pred'_p\\
        		%
@@
        		\land v\!=\!v_{px} \land
-       		\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\\
+       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\\
        		%
@@
        		\land v_{px}\!=\!v_{pxy}\\\hspace{3em}~ \land
-       		\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\big))
+       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\big))
        		\land v\!=\!v_{px} \land
-       		\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\\
+       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\\
        		%
@@
        		\land v\!=v_{px}\!=\!v_{pxy}\\\hspace{3em}~ \land
-       		\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}
+       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}
        		\land
-       		\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\big)
+       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\big)
        		$
@@
 substitutions  and of the predicates, we have:\\
-       	$\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\land 
-       	\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
+       	$\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\land 
+       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
        	= 
-       	\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land
-       	\Pred_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
-       	\implies\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
-       	= \Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}} $
+       	\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land
+       	\Pred_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
+       	\implies\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
+       	= \Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}} $
 
@@
 \land v\!=v_{px}\!=\!v_{pxy}\\~\hspace{3em}~ \land
-\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\big)\big)
+\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\big)\big)
 \\
@@
 \land v\!=\!v_{pxy} \land
-\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
+\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
   \end{small}
@@
        	the role 
-       	of $s^1$ and $s^3$ in the definition of $\mathcal{R}''$ is symmetrical, and thus 
+       	of $s$ and $u$ in the definition of $\mathcal{R}''$ is symmetrical, and thus 
        	the 

### 2017-11-15 2016-Weak-FH-Bisim/WeakBisim.tex
Some s.t.u missing in def of bisim

@@
     }
-    {\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle
+    {\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
     	\models
@@
 \begin{minipage}{0.69\linewidth} 	Suppose that
-   $A_1 = <L_1,J,\mathcal{S}_1, s^1_0,
-   \mathcal{T}_1>$ and $A_2 = <L_2,J,\mathcal{S}_2,s^2_0, \mathcal{T}_2>$
+   $A_1 = <L_1,J,\mathcal{S}_1, s_0,
+   \mathcal{T}_1>$ and $A_2 = <L_2,J,\mathcal{S}_2,t_0, \mathcal{T}_2>$
    are open automata where the set
@@
 $\mathcal{R}$ is an FH-bisimulation iff for any  states
-$s^1\in\mathcal{S}_1$ and $s^2\in\mathcal{S}_2$, $(s^1,s^2|\Pred)\in\mathcal{R}$, we 
+$s\in\mathcal{S}_1$ and $t\in\mathcal{S}_2$, $(s,t|\Pred)\in\mathcal{R}$, we 
 have
@@
      \inferrule*[myfraction=\reddottedrule]
-         {\{s^1_i\xrightarrow{a_i}_i s^{1'}_i\}^{i\in I_1}, % , s^1_i,s^{1'}_i\in 
+         {\{s_i\xrightarrow{a_i}_i s'_i\}^{i\in I_1}, % , s_i,s'_i\in 
          %States(I_1)
            \{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
-         {s^1 \OTarrow {v} s^{1'}}
+         {s \OTarrow {v} s'}
 
@@
     \inferrule*[myfraction=\reddottedrule]
-         {\{s^{2}_i\xrightarrow{a_{i x}}_i s^{2}_{i x}\}^{i\in I_{2 x}},
+         {\{t_i\xrightarrow{a_{i x}}_i t_{i x}\}^{i\in I_{2 x}},
            \{\xrightarrow{b_{j x}}_j\}^{j\in J_{2x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {s^2 \OTarrow {v_x} s^{2}_x}
+         {t \OTarrow {v_x} t_x}
 %         \right)
 \end{mathpar}
- such that  $\forall x, J_1=J_{2x}, (s^{1'},s^{2}_x|\Pred_{s^{1'},s^{2}_x})\in 
+ such that  $\forall x, J_1=J_{2x}, (s',t_x|\Pred_{s',t_x})\in 
  \mathcal{R}$; 
@@
      \land v\!=\!v_x \land  
-     \Pred_{s^{1'},s^{2}_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
+     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
      %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
@@
 
- \item  and symmetrically any open transition from $s^2$ in $\mathcal{T}_2$ can be 
-      covered by a set of transitions from $t^1$ in $\mathcal{T}_1$.
+ \item  and symmetrically any open transition from $t$ in $\mathcal{T}_2$ can be 
+      covered by a set of transitions from $s$ in $\mathcal{T}_1$.
  \end{itemize}
@@
    $\mathcal{R}$ is an Weak FH-bisimulation iff for any  states
-$s^1\in\mathcal{S}_1$ and\\
-$s^2\in\mathcal{S}_2$, $(s^1,s^2|\Pred)\in\mathcal{R}$, we 
+$s\in\mathcal{S}_1$ and\\
+$t\in\mathcal{S}_2$, $(s,t|\Pred)\in\mathcal{R}$, we 
    have the following:
@@
      \inferrule*[myfraction=\reddottedrule]
-         {\{s^1_i\xrightarrow{a_i}_i s^{1'}_i\}^{i\in I_1},
+         {\{s_i\xrightarrow{a_i}_i s'_i\}^{i\in I_1},
            \{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
-         {s^1 \OTarrow {v} s^{1'}}
+         {s \OTarrow {v} s'}
 
@@
     \inferrule*[myfraction=\reddottedrule]
-         {\{s^{2}_i\xrightarrow{a_{i x}}_i s^{2}_{i x}\}^{i\in I_{2 x}},
+         {\{t_i\xrightarrow{a_{i x}}_i t_{i x}\}^{i\in I_{2 x}},
            \{\xrightarrow{b_{j x}}_j\}^{j\in J_{2x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {s^2 \OTWeakarrow {v_x} s^{2'}_x}
+         {t \OTWeakarrow {v_x} t_x}
 \end{mathpar}
- such that  $\forall x, J_1=J_{2x}, (s^{1'},s^{2'}_x|\Pred_{s^{1'},s^{2'}_x})\in \mathcal{R}$; 
+ such that  $\forall x, J_1=J_{2x}, (s',t_x|\Pred_{s^{1'},t_x})\in \mathcal{R}$; 
  and  \\
@@
      \land v\!=\!v_x \land  
-     \Pred_{s^{1'},s^{2'}_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
-
- \item  and symmetrically any open transition from $s^2$ in $\mathcal{T}_2$ can be 
-      covered by a set of weak transitions from $t^1$ in $\mathcal{T}_1^*$.
+     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
+
+ \item  and symmetrically any open transition from $t$ in $\mathcal{T}_2$ can be 
+      covered by a set of weak transitions from $s$ in $\mathcal{T}_1^*$.
  \end{itemize}

### 2017-11-21 2017-Xudong-SMT/checker.tex
Add the checker.tex
This file describes the submission to Z3 module.

\documentclass[a4paper]{llncs}

\usepackage[T1]{fontenc}
%\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\geometry{a4paper}                   % ... or a4paper or a5paper or ...
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}

%\usepackage{amsfonts}
%\usepackage{fancyhdr}
%\usepackage{cite}
%\usepackage{ifthen}
%\usepackage{amssymb}
%\usepackage{fancyhdr}
%\usepackage{pifont}
\usepackage{stmaryrd}
\usepackage{mathtools,mathpartir}
\usepackage{proof}
%\usepackage{setspace}
%\usepackage{indentfirst}
\usepackage{amsmath,amssymb,amscd,mathrsfs}
\usepackage{array,booktabs,arydshln,xcolor}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
\usepackage{epsfig,color,subfigure,enumitem}
\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
\newcommand{\NOTE}[1]{\textcolor{blue}{\textbf{[NOTE:#1]}}}
\newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
\newcommand{\LUDO}[1]{\textcolor{green}{#1}}
\definecolor{airforceblue}{rgb}{0.26, 0.44, 0.56}
\newcommand{\QIN}[1]{\textcolor{airforceblue}{#1}}
\newcommand{\coloncolon}{{:\hspace{-.2ex}:}}
\makeatletter
\newcommand{\raisemath}[1]{\mathpalette{\raisem@th{#1}}}
\newcommand{\raisem@th}[3]{\raisebox{#1}{$#2#3$}}
\makeatother

\usepackage{macrospNets}

\def\AlgT{\mathcal{T}}
\def\AlgE{\mathcal{E}}
\def\AlgA{\mathcal{A}}
\def\AlgAS{\mathcal{A}_S}
\def\AlgB{\mathcal{B}}
\def\AlgI{\mathcal{I}}
\newcommand{\set}[1]{\overline{#1}}
\newcommand{\Pred}{\symb{Pred}}
\newcommand{\Post}{\symb{Post}}
%\usepackage[math]{cellspace}
%\setlength\cellspacetoplimit{ 37pt}
%\setlength\cellspacebottomlimit{18pt}

\pagestyle{plain}
% addition to the mathpartir package for red dotted rules,
% that we use for open-transitions
\makeatletter
\def \dotover {\textcolor{red}{\leavevmode\cleaders\hb@xt@ .22em{\hss $\cdot$\hss}\hfill\kern\z@}}
\def \reddottedrule #1#2{\hbox {\advance \hsize by -0.5em
%\sbox0{$\genfrac{}{}{0pt}{0}{#1}{#2}$} \phantom{\copy0} %
 {\ooalign{\vphantom{$\genfrac{}{}{0pt}{0}{#1}{#2}$}\cr\dotover\cr$\genfrac{}{}{0pt}{0}{#1}{#2}$\cr}}}}

 \def \dottedrule #1#2 {
  {\sbox0{$\genfrac{}{}{0pt}{0}{#1}{#2}$}%
    \vphantom{\copy0}%
    \ooalign{%
      \hidewidth
      $\vcenter{\moveright\nulldelimiterspace
        \hbox to\wd0{%
         \xleaders\hbox{\kern.5pt\vrule height 0.4pt width 1.5pt\kern.5pt}\hfill
          \kern-1.5pt
        }%
      }$
      \hidewidth\cr
    \box0\cr}}
}

\let \defaultfraction \mpr@@fraction
\makeatother

%\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}[theorem]{Proposition}
\newtheorem{cor}[theorem]{Corollary}
%\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{algorithm}[theorem]{Algorithm}
%\newtheorem{remark}[theorem]{Remark}
%\newtheorem{definition}[theorem]{Definition}
%\newtheorem{example}[theorem]{Example}
%\newtheorem{problem}[theorem]{Problem}
%\newtheorem{proof}[theorem]{Proof}

% Macros for the SOS rules and proof trees:
%\newcommand\openrule[2]{\redinfer{#1}{#2}}
\newcommand\openrule[2]{\inferrule*[myfraction=\reddottedrule,center]{#1}{#2}}
%\newcommand\openrule[2]{\inferrule*{#1}{#2}}
%\newcommand\ostate[1]{\triangleleft{\;#1\;}\triangleright}
\newcommand\ostate[1]{\triangleleft{#1}\triangleright}
\newcommand{\sm}[1]{\mbox{\boldmath\small #1}}
\DeclareMathOperator{\card}{card}
\DeclareMathOperator{\Flat}{Flat}
\renewcommand{\P}{\mathcal P}

\begin{document}
\section{Type system}
The SMT solver Z3 already has conservative type rules and checks type safety in Horn logic. When translating the pNets into SMT-LIB language, pNets should also make sure that
the term matching other term in SMT-LIB language will be correct in type checking. In next two section, we give out the presentation of the pNets and the type rules of them to ensure the type safety. 
\subsection{Algebra Presentation}
We have a set of basic algebra presentation for the pNet, including three basic sorts $Bool$, $Action$ and $Int$ and their own operators(constants as operators with no argument).
\begin{table}\caption{\leftline{Algebra Presentation}}
	\begin{tabular}{p{4cm}p{8cm}}
		\hline\specialrule{0em}{1pt}{1pt}
		Sort & Operator \\\specialrule{0em}{1pt}{1pt}
		\hdashline\specialrule{0em}{3pt}{3pt}
		Bool    			& $=,\ \ne,\ \land,\ \lor,\ \texttt{true},\ \texttt{false}$ 								\\\specialrule{0em}{1pt}{1pt}
		Action 			& $=,\ \ne,\ \texttt{FUN}$ 																	\\\specialrule{0em}{1pt}{1pt}
		Int 				& $=,\ \ne,\ - \texttt{(unary)},\ +,\ - \texttt{(binary)},\ \times,\ \div,\ \texttt{Nat}$ 			\\\specialrule{0em}{1pt}{1pt}
		\hline
	\end{tabular}
\end{table}

\subsection{Type Rule}
The environment is a set of variables with their own types like $x_1 : A_1, ... , x_n : A_n$. And use dom$(\Gamma)$ dedicate the collection of $x_1, ... , x_n$. Let $\mathcal{P}$ to be the presentation of the pNet.
\begin{table}\caption{\leftline{Judgments for Open pNets}}
	\begin{tabular}{p{5cm}p{7cm}}
		\hline\specialrule{0em}{3pt}{3pt}
		$\Gamma \vdash \diamond$ 					& $\Gamma$ is a well-formed environment 					\\\specialrule{0em}{1pt}{1pt}
		$\Gamma \vdash A$ 							& A is a well-formed type in $\Gamma$	 					\\\specialrule{0em}{1pt}{1pt}
		$\Gamma \vdash M: A$ 						& M is a well-formed term of type A in $\Gamma$			\\\specialrule{0em}{1pt}{1pt}
		\specialrule{0em}{3pt}{3pt}\hline
	\end{tabular}
\end{table}

\begin{table}\caption{\leftline{Type Rules for Open pNets}}
	\begin{tabular}{p{5cm}p{5cm}p{2.5cm}}
		\hline\specialrule{0em}{3pt}{3pt}
		(Env $\varnothing$) 								
		& 										
		&					\\\specialrule{0em}{1pt}{1pt}
            $\dfrac{ }{\varnothing \vdash \diamond}$			
            & %$\dfrac{\Gamma \vdash A ~~ x\ }{\varnothing \vdash \diamond}$
            &					\\\specialrule{0em}{3pt}{3pt}
		(Type Bool) 										
		&(Type Action) 						
		&(Type Int)			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash Bool~~\Gamma \vdash \diamond}{\mathcal{P},\Gamma \vdash Bool}$ 
		& $\dfrac{\mathcal{P} \vdash Action~~\Gamma \vdash \diamond}{\mathcal{P},\Gamma \vdash Action}$ 
		& $\dfrac{\mathcal{P} \vdash Int~~\Gamma \vdash \diamond}{\mathcal{P},\Gamma \vdash Int}$        \\\specialrule{0em}{3pt}{3pt}
		(Var x) 										
		& 						
		&			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash A~~\Gamma \vdash x:A}{\mathcal{P},\Gamma \vdash x:A}$ 
		&  
		&       		\\\specialrule{0em}{5pt}{5pt}
		(Expr $\land$)								
		&					
		& 			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash \land :: Bool, Bool \rightarrow Bool ~~\Gamma \vdash x_1:Bool ~~\Gamma \vdash x_2:Bool}{\mathcal{P},\Gamma \vdash x_1 \land x_2:Bool}$ 
		& 
		&       		\\\specialrule{0em}{5pt}{5pt}
		(Expr $\lor$)							
		&					
		& 			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash \lor :: Bool, Bool \rightarrow Bool ~~\Gamma \vdash x_1:Bool ~~\Gamma \vdash x_2:Bool}{\mathcal{P},\Gamma \vdash x_1 \lor x_2:Bool}$ 
		& 
		&       		\\\specialrule{0em}{5pt}{5pt}
		(Expr +)							
		&					
		& 			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash + :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1 + x_2:Int}$ 
		& 
		&       		\\\specialrule{0em}{5pt}{5pt}
		(Expr $\times$)							
		&					
		& 			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash \times :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1 \times x_2:Int}$ 
		& 
		&       		\\\specialrule{0em}{5pt}{5pt}
		(Expr $\div$)							
		&					
		& 			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash \div :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1 \div x_2:Int}$ 
		& 
		&       		\\\specialrule{0em}{5pt}{5pt}
		(Overloading)							
		&					
		& 			\\\specialrule{0em}{3pt}{3pt}
		(Overload =)							
		&					
		& 			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash A ~~\mathcal{P} \vdash = :: A, A \rightarrow Bool ~~\Gamma \vdash x_1:A ~~\Gamma \vdash x_2:A}{\mathcal{P},\Gamma \vdash x_1 = x_2:Bool}$ 
		& 
		&       		\\\specialrule{0em}{5pt}{5pt}
		(Overload $\ne$)							
		&					
		& 			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash A ~~\mathcal{P} \vdash \ne :: A, A \rightarrow Bool ~~\Gamma \vdash x_1:A ~~\Gamma \vdash x_2:A}{\mathcal{P},\Gamma \vdash x_1 \ne x_2:Bool}$ 
		& 
		&       		\\\specialrule{0em}{5pt}{5pt}
		(Polymorphism)							
		&					
		& 			\\\specialrule{0em}{3pt}{3pt}
		(Poly -)							
		&					
		& 			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash - :: Int \rightarrow Int ~~\Gamma \vdash x:Int}{\mathcal{P},\Gamma \vdash -x:Int}$  
		&$\dfrac{\mathcal{P} \vdash - :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1-x_2:Int}$ 
		&       		\\\specialrule{0em}{5pt}{5pt}
		(Poly $\texttt{FUN}$)							
		&					
		& 			\\\specialrule{0em}{1pt}{1pt}
		$\dfrac{\mathcal{P} \vdash \texttt{FUN} :: A_1,...,A_n \rightarrow Action ~~\mathcal{P} \vdash A_1~~...~~\mathcal{P} \vdash A_n ~~\Gamma \vdash x_1:A_1~~...~~\Gamma \vdash x_n:A_n}{\mathcal{P},\Gamma \vdash \texttt{FUN}(x_1,...,x_n):Action}$ 
		& 
		&			\\
		\specialrule{0em}{5pt}{5pt}\hline
	\end{tabular}
\end{table}

\subsection{Map to SMT-LIB language}
The pNet semantics can be full translated into SMT-LIB language, though some difference on defining functions exist.
\begin{table}\caption{\leftline{Mapping}}
	\begin{tabular}{p{3cm}p{9cm}}
		\hline\specialrule{0em}{5pt}{5pt}			
		(Presentation)							
		&								\\\specialrule{0em}{5pt}{5pt}		
		&$Sort \lhook\joinrel\longrightarrow$	declare-datatypes				\\\specialrule{0em}{3pt}{3pt}
		&$Operator \lhook\joinrel\longrightarrow$	declare-function		\\\specialrule{0em}{3pt}{3pt}
		(Checking)							
		&								\\\specialrule{0em}{5pt}{5pt}
		&$dom(\Gamma) \lhook\joinrel\longrightarrow$	declare-const		\\\specialrule{0em}{3pt}{3pt}
		&$Pred \lhook\joinrel\longrightarrow$	 assert		\\\specialrule{0em}{3pt}{3pt}
		(Expressions)							
		&								\\\specialrule{0em}{5pt}{5pt}
		&$\texttt{FUN}(x_1,...,x_n)$		\\\specialrule{0em}{3pt}{3pt}
		&$x_1- x_n$  $~~~~~~~\lhook\joinrel\longrightarrow$ declare-function	\\\specialrule{0em}{3pt}{3pt}
		&$...$	\\\specialrule{0em}{3pt}{3pt}
		\specialrule{0em}{5pt}{5pt}\hline
	\end{tabular}
\end{table}

\section{Submission to Z3}
\subsection{Z3 Notations}
Our semantic has already got enough informations for Z3 checking. Z3 has a number of notations for various usages. We only list the notations we needed in our algorithm as follows:
\TODO{Finish the description.}
\begin{enumerate}
\item \texttt{declare-datatypes}
\item \texttt{declare-function}
\item \texttt{declare-const}
\item \texttt{assert}
\end{enumerate}

\subsection{Submission of Algebra}
Before the submission of the open transitions to Z3, the user-inputed algebra of the pNet should be known at first. It gives Z3 informations of the sorts of the expression and the operators, corresponding to the  
\texttt{declare-datatypes} and \texttt{declare-function}. We declare the algebra in Z3 logic through Z3 API methods having the same effect as the notations. At the same time, we have several internal lists (actually hash maps) \texttt{exprs}, \texttt{funcDecls}, \texttt{sortDatatypes} to store the generated Z3 objects with their names for later proofs.

\subsection{Submission of Open Transitions}
Each time we submit each open transition to Z3 module, we translate its predicate into Z3 language format and send it for satisfiability checking. Every term of the predicate is declared as an \texttt{assert} in Z3. A constant action or a parameterized expression is easy to get from the internal list storing the objects while all the variables are not declared at the beginning. So we declare them before the submission of a predicate term with the API method conducting \texttt{declare-const}.

\subsection{Other works}
\paragraph{Quantifier}
\paragraph{Filter the State without Precursor}

\end{document}

### 2017-11-22 2017-Xudong-SMT/checker.tex
Update the checker.tex.
Modify the content after the skype on Nov.21st.

@@
 		\hdashline\specialrule{0em}{3pt}{3pt}
-		Bool    			& $=,\ \ne,\ \land,\ \lor,\ \texttt{true},\ \texttt{false}$ 								\\\specialrule{0em}{1pt}{1pt}
+		Bool    			& $=,\ \ne,\ \land,\ \lor,\ \texttt{true},\ \texttt{false},\ \texttt{FUN}$ 								\\\specialrule{0em}{1pt}{1pt}
 		Action 			& $=,\ \ne,\ \texttt{FUN}$ 																	\\\specialrule{0em}{1pt}{1pt}
-		Int 				& $=,\ \ne,\ - \texttt{(unary)},\ +,\ - \texttt{(binary)},\ \times,\ \div,\ \texttt{Nat}$ 			\\\specialrule{0em}{1pt}{1pt}
+		Int 				& $=,\ \ne,\ - \texttt{(unary)},\ +,\ - \texttt{(binary)},\ \times,\ \div,\ \texttt{Nat},\ \texttt{FUN}$ 			\\\specialrule{0em}{1pt}{1pt}
 		\hline
@@
 		&       		\\\specialrule{0em}{5pt}{5pt}
-		(Expr $\land$)								
+		(Expr Unary)								
 		&					
 		& 			\\\specialrule{0em}{1pt}{1pt}
-		$\dfrac{\mathcal{P} \vdash \land :: Bool, Bool \rightarrow Bool ~~\Gamma \vdash x_1:Bool ~~\Gamma \vdash x_2:Bool}{\mathcal{P},\Gamma \vdash x_1 \land x_2:Bool}$ 
+		$\dfrac{\mathcal{P} \vdash A ~~\mathcal{P} \vdash op :: A \rightarrow A ~~\Gamma \vdash x:A}{\mathcal{P},\Gamma \vdash op~x:A}$ 
 		& 
 		&       		\\\specialrule{0em}{5pt}{5pt}
-		(Expr $\lor$)							
+		(Expr Binary)							
 		&					
 		& 			\\\specialrule{0em}{1pt}{1pt}
-		$\dfrac{\mathcal{P} \vdash \lor :: Bool, Bool \rightarrow Bool ~~\Gamma \vdash x_1:Bool ~~\Gamma \vdash x_2:Bool}{\mathcal{P},\Gamma \vdash x_1 \lor x_2:Bool}$ 
+		$\dfrac{\mathcal{P} \vdash A ~~\mathcal{P} \vdash op :: A, A \rightarrow A ~~\Gamma \vdash x_1:A ~~\Gamma \vdash x_2:A}{\mathcal{P},\Gamma \vdash x_1~op~ x_2:A}$ 
 		& 
 		&       		\\\specialrule{0em}{5pt}{5pt}
-		(Expr +)							
-		&					
-		& 			\\\specialrule{0em}{1pt}{1pt}
-		$\dfrac{\mathcal{P} \vdash + :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1 + x_2:Int}$ 
-		& 
-		&       		\\\specialrule{0em}{5pt}{5pt}
-		(Expr $\times$)							
-		&					
-		& 			\\\specialrule{0em}{1pt}{1pt}
-		$\dfrac{\mathcal{P} \vdash \times :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1 \times x_2:Int}$ 
-		& 
-		&       		\\\specialrule{0em}{5pt}{5pt}
-		(Expr $\div$)							
-		&					
-		& 			\\\specialrule{0em}{1pt}{1pt}
-		$\dfrac{\mathcal{P} \vdash \div :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1 \div x_2:Int}$ 
-		& 
-		&       		\\\specialrule{0em}{5pt}{5pt}
-		(Overloading)							
+%		(Expr +)							
+%		&					
+%		& 			\\\specialrule{0em}{1pt}{1pt}
+%		$\dfrac{\mathcal{P} \vdash + :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1 + x_2:Int}$ 
+%		& 
+%		&       		\\\specialrule{0em}{5pt}{5pt}
+%		(Expr $\times$)							
+%		&					
+%		& 			\\\specialrule{0em}{1pt}{1pt}
+%		$\dfrac{\mathcal{P} \vdash \times :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1 \times x_2:Int}$ 
+%		& 
+%		&       		\\\specialrule{0em}{5pt}{5pt}
+%		(Expr $\div$)							
+%		&					
+%		& 			\\\specialrule{0em}{1pt}{1pt}
+%		$\dfrac{\mathcal{P} \vdash \div :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1 \div x_2:Int}$ 
+%		& 
+%		&       		\\\specialrule{0em}{5pt}{5pt}
+		(Polymorphism)							
 		&					
 		& 			\\\specialrule{0em}{3pt}{3pt}
-		(Overload =)							
+		(Poly =)							
 		&					
@@
 		&       		\\\specialrule{0em}{5pt}{5pt}
-		(Overload $\ne$)							
+		(Poly $\ne$)							
 		&					
@@
 		&       		\\\specialrule{0em}{5pt}{5pt}
-		(Polymorphism)							
-		&					
-		& 			\\\specialrule{0em}{3pt}{3pt}
-		(Poly -)							
-		&					
-		& 			\\\specialrule{0em}{1pt}{1pt}
-		$\dfrac{\mathcal{P} \vdash - :: Int \rightarrow Int ~~\Gamma \vdash x:Int}{\mathcal{P},\Gamma \vdash -x:Int}$  
-		&$\dfrac{\mathcal{P} \vdash - :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1-x_2:Int}$ 
-		&       		\\\specialrule{0em}{5pt}{5pt}
+%		(Poly -)							
+%		&					
+%		& 			\\\specialrule{0em}{1pt}{1pt}
+%		$\dfrac{\mathcal{P} \vdash - :: Int \rightarrow Int ~~\Gamma \vdash x:Int}{\mathcal{P},\Gamma \vdash -x:Int}$  
+%		&$\dfrac{\mathcal{P} \vdash - :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1-x_2:Int}$ 
+%		&       		\\\specialrule{0em}{5pt}{5pt}
 		(Poly $\texttt{FUN}$)							
@@
 		& 			\\\specialrule{0em}{1pt}{1pt}
-		$\dfrac{\mathcal{P} \vdash \texttt{FUN} :: A_1,...,A_n \rightarrow Action ~~\mathcal{P} \vdash A_1~~...~~\mathcal{P} \vdash A_n ~~\Gamma \vdash x_1:A_1~~...~~\Gamma \vdash x_n:A_n}{\mathcal{P},\Gamma \vdash \texttt{FUN}(x_1,...,x_n):Action}$
+		$\dfrac{\mathcal{P} \vdash \texttt{FUN} :: A_1,...,A_n \rightarrow A ~~\mathcal{P} \vdash A_1~~...~~\mathcal{P} \vdash A_n ~~\mathcal{P} \vdash A ~~\Gamma \vdash x_1:A_1~~...~~\Gamma \vdash x_n:A_n}{\mathcal{P},\Gamma \vdash \texttt{FUN}(x_1,...,x_n):A}$
 		& 

### 2017-11-23 2016-Weak-FH-Bisim/WeakBisim.tex

@@
 A pLTS is a tuple
-$pLTS\triangleq\mylangle S,s_0, \to\myrangle$ where:
+$\pLTS\triangleq\mylangle S,s_0, \to\myrangle$ where:
 \begin{itemize}
@@
 A pNet is a hierarchical structure where leaves are pLTSs and holes:\\
-$\pNet\triangleq pLTS~|~\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in 
+$\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in 
 K}\myrangle$
@@
 	An \emph{open automaton} is a structure\\ $A =
-	<LTS_i^{i\in I},J,\mathcal{S},s_0,\mathcal{T}>$ where:
+	<\LTS_i^{i\in I},J,\mathcal{S},s_0,\mathcal{T}>$ where:
 	\begin{itemize}
 		\item[$\bullet$]  $I$ and $J$ are  sets of indices,
-		\item[$\bullet$]  $LTS_i^{i\in I}$ is a family of LTSs,
+		\item[$\bullet$]  $\LTS_i^{i\in I}$ is a family of LTSs,
 		\item[$\bullet$]   $\mathcal{S}$ is a set of states and $s_0$ an initial state
@@
 		$t\in \mathcal{T}$ there exist $I'$, $J'$ with $I'\subseteq I$, $J'
-		\subseteq J$, such that $t$ is an open transition over $LTS_i^{i\in I'}$, $J'$,
+		\subseteq J$, such that $t$ is an open transition over $\LTS_i^{i\in I'}$, $J'$,
 		and  $\mathcal{S}$.
@@
     	%\land
-    	%Leaves(\pNet_m) = \overline{pLTS}^{L_k})
+    	%Leaves(\pNet_m) = \overline{\pLTS}^{L_k})
     	\\
@@
 
-Let \ERIC{$\mathcal{R}=\{(s^1,s^2|\Pred_{s^1,s^2})\}$} be a relation over the set $\mathcal{S}_1$ and $\mathcal{S}_2$ constrained by a predicate
-More precisely, for any pair $(s^1,s^2)$, there is a 
+Let $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$ be a relation over the set $\mathcal{S}_1$ and 
+$\mathcal{S}_2$ constrained by a predicate
+More precisely, for any pair $(s,t)$, there is a 
    single
-      $(s^1,s^2|\Pred_{s^1,s^2})\in\mathcal{R}$  stating that $s^1$ and $s^2$ are related 
-      if $\Pred_{s^1,s^2}$ 
+      $(s,t|\Pred_{s,t})\in\mathcal{R}$  stating that $s$ and $t$ are related 
+      if $\Pred_{s,t}$ 
       is 
-      true, i.e. the states are related when the variables in $s^1$ and $s^2$ verify the 
-      predicate $\Pred_{s^1,s^2}$.
+      true, i.e. the states are related when the variables in $s$ and $t$ verify the 
+      predicate $\Pred_{s,t}$.
 
@@
 \begin{minipage}{0.69\linewidth} 	Suppose that
-   $A_1 = <L_1,J,\mathcal{S}_1, s_0,
-   \mathcal{T}_1>$ and $A_2 = <L_2,J,\mathcal{S}_2,t_0, \mathcal{T}_2>$
+   $A_1 = <\overline{\LTS_1},J,\mathcal{S}_1, s_0,
+   \mathcal{T}_1>$ and $A_2 = <\overline{\LTS_2},J,\mathcal{S}_2,t_0, \mathcal{T}_2>$
    are open automata where the set
@@
 	\includegraphics[width=\linewidth]{XFIG/Bisim}
+	\TODO{change fig: s1,s2 $\to$ s,t}
 \end{minipage}
@@
     \inferrule*[myfraction=\reddottedrule]
-         {\{t_i\xrightarrow{a_{i x}}_i t_{i x}\}^{i\in I_{2 x}},
-           \{\xrightarrow{b_{j x}}_j\}^{j\in J_{2x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {\{t_i\xrightarrow{a_{i x}}_i t_{i x}\}^{i\in I_{ x}},
+           \{\xrightarrow{b_{j x}}_j\}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
          {t \OTarrow {v_x} t_x}
@@
 \end{mathpar}
- such that  $\forall x, J_1=J_{2x}, (s',t_x|\Pred_{s',t_x})\in 
+ such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in 
  \mathcal{R}$; 
@@
 \begin{definition}[Weak open transitions]
-  Let $A = <L,J,\mathcal{S},s_0,\mathcal{T}>$ be an open automaton.
-  We define $\mathcal{T^*}$ the \emph{Weak open transition relation}
-  with respect to a set of invisible actions $\mathcal{Inv}$ as:
+  Let $A = <\overline{\LTS},J,\mathcal{S},s_0,\mathcal{T}>$ be an open automaton.
+  We define $\mathcal{T^*}$ the \emph{weak open transition relation}
+  with respect to a set of invisible actions $\mathcal{I}$ as:
 
@@
          {\{s_i\xrightarrow{a_i}_i s'_i\}^{i\in I_1}, 
-           \{\xrightarrow{b_j}_j\}^{j\in J},\Pred,\Post}
+           \{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred,\Post}
          {s \OTWeakarrow {v} s'}
@@
 
- \TODO{Pas si simple !!!}
+ \TODO{Pas si simple !!!!!!!!!!!!!!!!!!!}
 
@@
 Let $A_1$ and $A_2$ be open automata, and $\mathcal{R}$ a relation over
-$S_1$ and $S_2$, as in Definition \ref{def-FH-bisim}.
+$\mathcal{S}_1$ and $\mathcal{S}_2$, as in Definition \ref{def-FH-bisim}.
 
 Then 
-   $\mathcal{R}$ is an Weak FH-bisimulation iff for any  states
+   $\mathcal{R}$ is a weak FH-bisimulation iff for any  states
 $s\in\mathcal{S}_1$ and\\
@@
     \inferrule*[myfraction=\reddottedrule]
-         {\{t_i\xrightarrow{a_{i x}}_i t_{i x}\}^{i\in I_{2 x}},
-           \{\xrightarrow{b_{j x}}_j\}^{j\in J_{2x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {\{t_i\xrightarrow{a_{i x}}_i t_{i x}\}^{i\in I_{x}},
+           \{\xrightarrow{b_{j x}}_j\}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
          {t \OTWeakarrow {v_x} t_x}
 \end{mathpar}
- such that  $\forall x, J_1=J_{2x}, (s',t_x|\Pred_{s^{1'},t_x})\in \mathcal{R}$; 
+ such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
  and  \\
@@
         \emph{Suppose $\mathcal{R}$ 
-       	is an FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, 
+       	is an FH-bisimulation. Then $\mathcal{R}$ is an equivalence, that is, 
        	$\mathcal{R}$ is 
@@
        	\inferrule*[myfraction=\reddottedrule]
-       	{\{t_{p i}\xrightarrow{a_{p i x}}_i t_{p i x}\}^{i\in I_{2 p x}},
-       		\{\xrightarrow{b_{j p x}}_j\}^{j\in J_{2px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
+       	{\{t_{p i}\xrightarrow{a_{p i x}}_i t_{p i x}\}^{i\in I_{p x}},
+       		\{\xrightarrow{b_{j p x}}_j\}^{j\in J_{px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
        	{t_p \OTarrow {v_{px}} t_{p x}}
@@
 
-       	such that  $\forall x, J_1=J_{2px}, (s',t_{px}|\Pred_{{px}})\in 
+       	such that  $\forall x, J_1=J_{px}, (s',t_{px}|\Pred_{{px}})\in 
        	\mathcal{R}$;
@@
        	\inferrule*[myfraction=\reddottedrule]
-       	{\{u_i\xrightarrow{a_{i p x y}}_i u_{i p x y}\}^{i\in I_{3 p x y}},
-       		\{\xrightarrow{b_{j p x y}}_j\}^{j\in J_{3pxy}}, 
+       	{\{u_i\xrightarrow{a_{i p x y}}_i u_{i p x y}\}^{i\in I_{p x y}},
+       		\{\xrightarrow{b_{j p x y}}_j\}^{j\in J_{pxy}}, 
        		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
@@
        	\end{mathpar}
-       	such that  $\forall y, J_{2px}=J_{3pxy}, 
+       	such that  $\forall y, J_{px}=J_{pxy}, 
        	(t_{px},u_{pxy}|\Pred_{{pxy}})\in \mathcal{R}'$; and  \\
@@
 
-       	First, $\forall y, \forall x, \forall p, J_1=J_{2px}=J_{3pxy}, 
-       	({s}',s_{pxy}|\Pred\,'_{{pxy}})\in \mathcal{R}''$. 
+       	First, $\forall y, \forall x, \forall p, J_1=J_{px}=J_{pxy}, 
+       	({s}',u_{pxy}|\Pred\,'_{{pxy}})\in \mathcal{R}''$. 
        	Indeed for any 
@@
        	$(s',t_{px}|\Pred_{{px}})\in \mathcal{R}$
-       	and $(t_{px},u_{pxy}|\Pred{{pxy}})\in \mathcal{R}'$. 
+       	and $(t_{px},u_{pxy}|\Pred_{{pxy}})\in \mathcal{R}'$. 
        	More precisely, $t_{px} \in ({t_p}')^{p\in P'}$ where $({t_p}')^{p\in 
@@
 
-       	Second, we need \\
+       	Second, by definition of bisimulation we need (recall that $\Pred\,''$ is the 
+       	original predicate relating $s$ and $u$ by definition of the transitive 
+       	closure):\\
        	\begin{small}
@@
        	\begin{small}
-       		$\Pred_p \land \Pred_{OT}\land\Pred'_p\\
+       		$\Pred_p \land \Pred_{OT}\land\Pred_p\!'\\
        		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
@@
        		\land v\!=\!v_{px} \land
-       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\land\Pred'_p\\
+       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\land\Pred_p\!'\\
        		%
        		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-       		\left( \forall j. b_j=b_{jpx}  \Rightarrow (\Pred_{OT_{px}}\land\Pred'_p)
+       		\left( \forall j. b_j=b_{jpx}  \Rightarrow (\Pred_{OT_{px}}\land\Pred_p\!')
        		\land v\!=\!v_{px} \land
@@
        	\implies\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
-       	= \Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}} $
+       	= \Pred\!'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}} $
 
        	This allows us to conclude, with $\Pred\,'' = \bigvee_{p\in P} 
-       	\Pred_p\land\Pred_p\,'$:
+       	\Pred_p\land\Pred_p\!'$:
          	\begin{small}     	
@@
 \hspace{1cm} \implies\!\!\! \bigvee_{p\in P} (
-\Pred_p\land\Pred_p\,' \land \Pred_{OT})\\
+\Pred_p\land\Pred_p\!' \land \Pred_{OT})\\
 \hspace{1cm} \implies\!\!\!\bigvee_{p\in P}

### 2017-11-23 2017-Xudong-SMT/checker-eric/checker.tex
Creation of document "checker-eric"

--- 2017-11-22 2017-Xudong-SMT/checker.tex
@@
 \usepackage{amsmath,amssymb,amscd,mathrsfs}
-\usepackage{array,booktabs,arydshln,xcolor}
+% \usepackage{array,booktabs,arydshln,xcolor}
+\usepackage{array,booktabs,xcolor}
 \DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
@@
 \begin{document}
+
+This document presumes the definition of Term algebras and
+parameterized actions from the pNet
+theory definition, that we will not repeat here.
+
+\section{Translations from pNets to SMTLib}
+In order to submit satisfiability problems to Z3 (for the predicates
+in open transitions), we need to generate SMTlib programs, from the
+pNet Algebra presentation and predicates.
+More precisely, we need to translate to SMTlib:
+\begin{itemize}
+  \item for a given pNet: the presentation of the action algebra
+    (sorts, operators, constants), 
+    \item for each open transition: the declaration of variables, and
+      the predicate (including action expressions).
+\end{itemize}
+
+During this translation, in order to guarantee that the generated code
+will cause no runtime errors during parsing and execution, we need
+to ensure that all objects used in the SMTlib code are properly
+declared, and that they are correctly typed.
+
 \section{Type system}
-The SMT solver Z3 already has conservative type rules and checks type safety in Horn logic. When translating the pNets into SMT-LIB language, pNets should also make sure that
-the term matching other term in SMT-LIB language will be correct in type checking. In next two section, we give out the presentation of the pNets and the type rules of them to ensure the type safety. 
-\subsection{Algebra Presentation}
-We have a set of basic algebra presentation for the pNet, including three basic sorts $Bool$, $Action$ and $Int$ and their own operators(constants as operators with no argument).
-\begin{table}\caption{\leftline{Algebra Presentation}}
+%% The SMT solver Z3 already has conservative type rules and checks type safety in Horn logic. When translating the pNets into SMT-LIB language, pNets should also make sure that
+%% the term matching other term in SMT-LIB language will be correct in
+%% type checking. In next two section, we give out the presentation of
+%% the pNets and the type rules of them to ensure the type safety.
+The type system in pNets is quite simple, the expressions are built
+from variables, constants, and operators of a many-sorted algebra, and
+we only need simple first-order polymorphic types.
+Additionaly, for convenience, we want to introduce some ``generic''
+operators in the algebra, with an overloading mechanism; as these do
+not exist in SMTlib, we will have a specific translation mechanism.
+
+Note that in principle, such an algebra correspond to a given
+high-level language (e.g. a process algebra), and that the algebra
+presentation will be defined once and for all in the framework of the
+pNet semantics of each specific language.
+
+\subsection{Algebra Presentations}
+
+We have a minimal, predefined algebra presentation for all pNets, including
+three basic sorts $Bool$, $Action$ and $Int$ and their
+operators. Table \ref{Table:predefinedSorts} defines these elements.
+
+\begin{table}\caption{\label{Table:predefinedSorts}\leftline{Algebra Presentation: predefined Sorts
+  and Operators}}
 	\begin{tabular}{p{4cm}p{8cm}}
 		\hline\specialrule{0em}{1pt}{1pt}
-		Sort & Operator \\\specialrule{0em}{1pt}{1pt}
-		\hdashline\specialrule{0em}{3pt}{3pt}
-		Bool    			& $=,\ \ne,\ \land,\ \lor,\ \texttt{true},\ \texttt{false},\ \texttt{FUN}$ 								\\\specialrule{0em}{1pt}{1pt}
-		Action 			& $=,\ \ne,\ \texttt{FUN}$ 																	\\\specialrule{0em}{1pt}{1pt}
-		Int 				& $=,\ \ne,\ - \texttt{(unary)},\ +,\ - \texttt{(binary)},\ \times,\ \div,\ \texttt{Nat},\ \texttt{FUN}$ 			\\\specialrule{0em}{1pt}{1pt}
-		\hline
+		Sort & Operator
+                \\\specialrule{0em}{1pt}{1pt}
+		\hline\specialrule{0em}{3pt}{3pt}
+		Bool    			&
+                $\land,\ \lor,\ \texttt{true},\ \texttt{false}$
+                \\\specialrule{0em}{1pt}{1pt} 
+		Action 			& \textsl{no predefined operator}
+                \\\specialrule{0em}{1pt}{1pt}
+		Int 				& $\ - \texttt{(unary)},\ +,\ -
+                \texttt{(binary)},\ \times,\ \div,\ {0, 1, ...} \in \texttt{Nat}$
+                \\\specialrule{0em}{1pt}{1pt}
+                \textsl{for any sort} & $=,\ \ne$
+		\\\hline
 	\end{tabular}
 \end{table}
+
+For a given language, or for a given use-case, the designer can
+declare more sorts and operators, using our pNet API.
+As an example, the CCS action algebra include:
 
@@
 		&       		\\\specialrule{0em}{5pt}{5pt}
-		(Expr Unary)								
-		&					
-		& 			\\\specialrule{0em}{1pt}{1pt}
-		$\dfrac{\mathcal{P} \vdash A ~~\mathcal{P} \vdash op :: A \rightarrow A ~~\Gamma \vdash x:A}{\mathcal{P},\Gamma \vdash op~x:A}$ 
-		& 
-		&       		\\\specialrule{0em}{5pt}{5pt}
-		(Expr Binary)							
-		&					
-		& 			\\\specialrule{0em}{1pt}{1pt}
-		$\dfrac{\mathcal{P} \vdash A ~~\mathcal{P} \vdash op :: A, A \rightarrow A ~~\Gamma \vdash x_1:A ~~\Gamma \vdash x_2:A}{\mathcal{P},\Gamma \vdash x_1~op~ x_2:A}$ 
-		& 
-		&       		\\\specialrule{0em}{5pt}{5pt}
-%		(Expr +)							
-%		&					
-%		& 			\\\specialrule{0em}{1pt}{1pt}
-%		$\dfrac{\mathcal{P} \vdash + :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1 + x_2:Int}$ 
-%		& 
-%		&       		\\\specialrule{0em}{5pt}{5pt}
-%		(Expr $\times$)							
-%		&					
-%		& 			\\\specialrule{0em}{1pt}{1pt}
-%		$\dfrac{\mathcal{P} \vdash \times :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1 \times x_2:Int}$ 
-%		& 
-%		&       		\\\specialrule{0em}{5pt}{5pt}
-%		(Expr $\div$)							
-%		&					
-%		& 			\\\specialrule{0em}{1pt}{1pt}
-%		$\dfrac{\mathcal{P} \vdash \div :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1 \div x_2:Int}$ 
-%		& 
-%		&       		\\\specialrule{0em}{5pt}{5pt}
-		(Polymorphism)							
+		\multispan{2} (Binary operators, e.g.: $\land, \lor$ for booleans, $+, -, \times, \div, \le, \ge$ for integers, etc.)
+
+		& 			\\\specialrule{0em}{3pt}{3pt}
+		$\dfrac{\mathcal{P} \vdash BinOp :: ty1, ty1 \rightarrow ty2 ~~\Gamma \vdash x_1:ty1 ~~\Gamma \vdash x_2:ty1}{\mathcal{P},\Gamma \vdash x_1 ~BinOp~ x_2:ty2}$ 
 		& 
 		&       		\\\specialrule{0em}{3pt}{3pt}
-		(Poly =)							
+		\multicolumn{2}{l}{(Unary operators, e.g. $\lnot$ for booleans, - for integers)}
+
+		& 			\\\specialrule{0em}{3pt}{3pt}
+		$\dfrac{\mathcal{P} \vdash UnOp :: ty1 \rightarrow ty2 ~~\Gamma \vdash x:ty1}{\mathcal{P},\Gamma \vdash Unop~x:ty2}$   
+		&&       		\\\specialrule{0em}{5pt}{5pt}
+		(Polymorphic EQ and NEQ)							
 		&					
-		& 			\\\specialrule{0em}{1pt}{1pt}
-		$\dfrac{\mathcal{P} \vdash A ~~\mathcal{P} \vdash = :: A, A \rightarrow Bool ~~\Gamma \vdash x_1:A ~~\Gamma \vdash x_2:A}{\mathcal{P},\Gamma \vdash x_1 = x_2:Bool}$ 
 		&
+                                         \\\specialrule{0em}{1pt}{1pt}
+		\multicolumn{2}{l}{(Note: I removed the $~~\mathcal{P} \vdash \ne :: A, A \rightarrow Bool$)}
+
+		&                        \\\specialrule{0em}{3pt}{3pt}
+		$\dfrac{\mathcal{P} \vdash A  ~~\Gamma \vdash x_1:A ~~\Gamma \vdash x_2:A}{\mathcal{P},\Gamma \vdash x_1 = x_2:Bool}$ 
+		& 
+		$\dfrac{\mathcal{P} \vdash A  ~~\Gamma \vdash x_1:A ~~\Gamma \vdash x_2:A}{\mathcal{P},\Gamma \vdash x_1 \ne x_2:Bool}$
+
 		&       		\\\specialrule{0em}{5pt}{5pt}
-		(Poly $\ne$)							
+		(Overloaded FUN)							
 		&					
-		& 			\\\specialrule{0em}{1pt}{1pt}
-		$\dfrac{\mathcal{P} \vdash A ~~\mathcal{P} \vdash \ne :: A, A \rightarrow Bool ~~\Gamma \vdash x_1:A ~~\Gamma \vdash x_2:A}{\mathcal{P},\Gamma \vdash x_1 \ne x_2:Bool}$ 
-		& 
-		&       		\\\specialrule{0em}{5pt}{5pt}
-%		(Poly -)							
-%		&					
-%		& 			\\\specialrule{0em}{1pt}{1pt}
-%		$\dfrac{\mathcal{P} \vdash - :: Int \rightarrow Int ~~\Gamma \vdash x:Int}{\mathcal{P},\Gamma \vdash -x:Int}$  
-%		&$\dfrac{\mathcal{P} \vdash - :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1-x_2:Int}$ 
-%		&       		\\\specialrule{0em}{5pt}{5pt}
-		(Poly $\texttt{FUN}$)							
-		&					
-		& 			\\\specialrule{0em}{1pt}{1pt}
-		$\dfrac{\mathcal{P} \vdash \texttt{FUN} :: A_1,...,A_n \rightarrow A ~~\mathcal{P} \vdash A_1~~...~~\mathcal{P} \vdash A_n ~~\mathcal{P} \vdash A ~~\Gamma \vdash x_1:A_1~~...~~\Gamma \vdash x_n:A_n}{\mathcal{P},\Gamma \vdash \texttt{FUN}(x_1,...,x_n):A}$
+		& 			\\\specialrule{0em}{3pt}{3pt}
+		$\dfrac{\mathcal{P} \vdash \texttt{FUN} :: A_1,...,A_n \rightarrow A ~~\mathcal{P} \vdash A_1~~...~~\mathcal{P} \vdash A_n ~~\Gamma \vdash x_1:A_1~~...~~\Gamma \vdash x_n:A_n}{\mathcal{P},\Gamma \vdash \texttt{FUN}(x_1,...,x_n):A}$
 		& 

### 2017-11-26 2017-Xudong-SMT/checker.tex
Update checker.tex
Add the draft of description of the format translation between pNet and Z3.

@@
-\documentclass[a4paper]{llncs}
+\documentclass[a4paper]{lncs/llncs}
 
@@
 \def\AlgI{\mathcal{I}}
-\newcommand{\set}[1]{\overline{#1}}
+%\newcommand{\set}[1]{\overline{#1}}
 \newcommand{\Pred}{\symb{Pred}}
@@
 \newcommand{\sm}[1]{\mbox{\boldmath\small #1}}
-\DeclareMathOperator{\card}{card}
-\DeclareMathOperator{\Flat}{Flat}
+%\DeclareMathOperator{\card}{card}
+%\DeclareMathOperator{\Flat}{Flat}
 \renewcommand{\P}{\mathcal P}
@@
 \end{table}
+
+\paragraph{Translation} from pNets informations into SMT-LIB language format is corresponded with the mapping rules.
+\subsubsection{Sort}
+There are several basic Sorts already defined in the presentation and users can declare more customized Sorts.
+In addition, Bool and Int type is also Z3 default datatypes.
+Sorts only provide their names to the datatype constructor in Z3, the more content will be added according to the Operators in the presentation.\\\\
+\centerline{$\texttt{(declare-datatypes\ ()\ (($SortName$\ ...\ )))}$}
+%(declare-datatypes () ((SortName ... )))
+\subsubsection{FUN function}
+The signature of the FUN operators are defined by users. But they still have a fixed format.\\\\
+\centerline{$\texttt{FUN} :: Type_1, ... ,Type_n \longrightarrow Type$}\\\\
+%(declare-fun FUN (TypeName_1, ... ,TypeName_n) TypeName)
+The types of all the arguments are given to the Z3, so does the return type, but written at another place.  We use a suffix after the "FUN" name to distinct different FUN operators.\\\\
+\centerline{$\texttt{(declare-fun\ FUN\_Type1...\_TypeN\_Type\ ($Type_1$\ ... \ $Type_n$)\ $Type$)}$}
 

### 2017-12-19 2016-Weak-FH-Bisim/WeakBisim.tex
OOPS forgot to commit meeting changes

@@
       predicate $\Pred_{s,t}$.
-
+      \TODO{LudoPred -> Pred s,t}
  FH-bisimulation is defined formally: 
@@
 automata that is an FH-bisimulation and their initial states are equivalent.
-
+\TODO{Ludo: define are equivalent : is in the relation les valeurs des variables des 
+etats initiaux verifient le predicat associe aux etats initiaux}
  \end{definition}
-Classically, $\Pred_{target_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}$
+Classically, $\Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}$
 applies in parallel the  
@@
 automata that is an Weak FH-bisimulation and their initial states are equivalent.
-
+\TODO{define equivalent}
  \end{definition}
@@
        	$\mathcal{T}_2$ relating $s$ and $u$, let $(t_p)^{p\in P}$ be this family.  
+       	       	We have $\Pred\,'' = \bigvee_{p\in P} \Pred_p\land\Pred_p\,'$.
+
+\medskip
 
@@
        	the 
-       	following by definition of bisimulation.
+       	following by definition of bisimulation:
        	For any open transition $OT$ in $\mathcal{T}_1$ originating from $s$.
-       	Additionally we have $\Pred\,'' = \bigvee_{p\in P} \Pred_p\land\Pred_p\,'$.
        	\begin{mathpar}

### 2017-12-19 2016-Weak-FH-Bisim/WeakBisim.tex
dessins
change nom d'un dessin
chasse prime

@@
 \begin{figure}[t]
-\begin{minipage}{6.1cm}
-
-  \includegraphics[width=\linewidth]{XFIG/Enable1}
-  \\[1.3ex]
- \includegraphics[width=\linewidth]{XFIG/Enable2}
-  \caption{Two pNet encodings for  Enable }  \label{schema:enable-pnets}
-\end{minipage}
-  \hspace{2mm}
-\begin{minipage}{6cm}
-  \includegraphics[width=\linewidth]{XFIG/P-QR}
-  \caption{Composed pNet for ``P>>(Q>>R)''}  \label{schema:enable-composed}
-\end{minipage}
+%\begin{minipage}{\linewidth}
+
+  \includegraphics[width=7cm]{XFIG/Transport}
+  \hspace{0.5cm}
+ \includegraphics[width=4.5cm]{XFIG/TransportSchema}
+  \caption{Schema and specification of the protocol }  \label{schema:enable-pnets}
+%\end{minipage}
+  \vspace{1cm}
+%\begin{minipage}{6cm}
+  \includegraphics[width=10cm]{XFIG/ABPSchema}
+  \caption{Composed pNet with the ABP protocol}  \label{schema:enable-composed}
+%\end{minipage}
 
@@
 
-       	The relation is built as follows: for each pair of state $s$, $u$, for each 
+       	The relation is built as follows: for each pair of states $s$, $u$, for each 
        	state 
@@
        	$\mathcal{T}_2$ relating $s$ and $u$, let $(t_p)^{p\in P}$ be this family.  
-       	       	We have $\Pred\,'' = \bigvee_{p\in P} \Pred_p\land\Pred_p\,'$.
+       	       	We have $\Pred\,'' = \bigvee_{p\in P} \Pred_p\land\Pred\,'_p$.
 
@@
        	More precisely, $t_{px} \in ({t_p}')^{p\in P'}$ where $({t_p}')^{p\in 
-       		P'}$ 
+       		P'}$ \TODO{Pas sure prime utile t, or p, or P}
        	is 
@@
 		\emptyset$).
-		 Then there exist $v_Q$, $\Pred'$, $\Pred''$, 
-		$\Post'$, $\Post''$ s.t.:\\[-2ex]
+		 Then there exist $v_Q$, $\Pred\,'$, $\Pred\,''$, 
+		$\Post\,'$, $\Post\,''$ s.t.:\\[-2ex]
 		%\[
@@
 				\{\xrightarrow{b_j}_j\}^{j\in J\setminus \Holes(Q) \cup \{j_0\}}, 
-				\Pred',  
-				\Post'}
+				\Pred\,',  
+				\Post\,'}
 			{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {v}
@@
 			{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I\cap L_Q},
-				\{\xrightarrow{b_j}_j\}^{j\in J\cap\Holes(Q)}, \Pred'',  
-				\Post''}
+				\{\xrightarrow{b_j}_j\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
+				\Post\,''}
 			{\ostate{s_i^{i\in L_Q}} \OTarrow {v_Q}
@@
 		\end{mathpar}
-		and  $\Pred\subst{v_Q\leftarrow b_{j_0}} =(\Pred'
-		\land \Pred'')$, $\Post=\Post'\uplus 
-		\Post''$ where $\Post''$ is the restriction of $\Post$ over variables of 
+		and  $\Pred\subst{v_Q\leftarrow b_{j_0}} =(\Pred\,'
+		\land \Pred\,'')$, $\Post=\Post'\uplus 
+		\Post\,''$ where $\Post\,''$ is the restriction of $\Post$ over variables of 
 		$\Leaves(Q)$.
@@
 			\{\xrightarrow{b_j}_j\}^{j\in J\cap\Holes(Q)}, \Pred_{j_0},  
-			\Post''}
+			\Post\,''}
 		{\ostate{s_i^{i\in L_Q}} \OTarrow {v_{j_0}}
@@
 This already ensures the second part of the conclusion if we 
-choose\footnotemark[\thefootnote]  $v_Q=v_{j_0}$ ($\Pred''= \Pred_{j_0}$). Now let $I'= 
+choose\footnotemark[\thefootnote]  $v_Q=v_{j_0}$ ($\Pred\,''= \Pred_{j_0}$). Now let $I'= 
 \biguplus I'_m=I\setminus L_Q$, $J'=\biguplus J'_m\uplus J_k 
 \uplus\{j_0\}=J\setminus\Holes(Q)\uplus \{j_0\}$; the predicate is 
-$\Pred'=\bigwedge_{m\in I_k}\Pred_m 
+$\Pred\,'=\bigwedge_{m\in I_k}\Pred_m 
 \land \Pred(SV,a_i^{i\in I_k},b_j^{j\in J_k\cup \{j_0\}},v)$
@@
 $\alpha_{j_0}=b_{j_0}$.
-Thus, $\Pred\subst{v_Q\leftarrow b_{j_0}}=(\Pred' 
-\land \Pred'')$. %\TODO{the argument on renaming has mostly been
+Thus, $\Pred\subst{v_Q\leftarrow b_{j_0}}=(\Pred\,' 
+\land \Pred\,'')$. %\TODO{the argument on renaming has mostly been
                  %removed is it still OK? yes.}. 
@@
 builts similarly as they only deal with  
-leaves): $\Post=\Post'\uplus \Post''$. This concludes the 
+leaves): $\Post=\Post\,'\uplus \Post\,''$. This concludes the 
 proof as we checked all the premises of the open transition for both $P$ and $Q$.\qed
@@
 		\{\xrightarrow{b_j}_j\}^{j\in J_Q},\\\\
-		 \Pred',  
-		\Post'}
+		 \Pred\,',  
+		\Post\,'}
 	{\ostate{s_i^{i\in L_Q}} \OTarrow {v_Q}
@@
 			\{\xrightarrow{b_j}_j\}^{j\in J\setminus\{j_0\} \uplus J_Q}, 
-			\Pred\subst{b_{j_0}\leftarrow v_Q}\land\Pred',  
-			\Post\uplus \Post'}
+			\Pred\subst{b_{j_0}\leftarrow v_Q}\land\Pred\,',  
+			\Post\uplus \Post\,'}
 		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {v}
@@
 J_m \uplus J_Q \uplus J_k = J\setminus\{j_0\}\uplus J_Q$. The predicate for the open 
-transition is: $\Pred''=\bigwedge_{m\in I_k}\Pred_m \land \Pred'
+transition is: $\Pred\,''=\bigwedge_{m\in I_k}\Pred_m \land \Pred\,'
 \land \Pred(SV,a_i^{i\in I_k}\uplus(j_0\mapsto v_Q),b_j^{j\in J_k},v)$. By definition 
@@
 	\forall i\in I_k.\, a_i=\alpha_i\land \forall j \in J_k.\, b_j=\alpha_j \land 
-	\alpha'_k=v\land v_Q=\alpha_{j_0}$, finally $\Pred''=\Pred\subst{b_{j_0}\leftarrow 
-	v_Q} \land \Pred'$. The post-condition gathers the post-conditions related to all 
+	\alpha'_k=v\land v_Q=\alpha_{j_0}$, finally $\Pred\,''=\Pred\subst{b_{j_0}\leftarrow 
+	v_Q} \land \Pred\,'$. The post-condition gathers the post-conditions related to all 
 	the leaves. Finally, the composed open transition can be
@@
  }\end{mathpar}
- and  $\Pred_{OT}\subst{v_Q\leftarrow b_{j_0}} =({\Pred\,}'
- \land {\Pred\,}'')$, $\Post_{OT}=\Post'\uplus 
- \Post''$ ($\Post''$ is the restriction of $\Post$ over variables of 
+ and  $\Pred_{OT}\subst{v_Q\leftarrow b_{j_0}} =({\Pred\,'}
+ \land {\Pred\,}'')$, $\Post_{OT}=\Post\,'\uplus 
+ \Post\,''$ ($\Post\,''$ is the restriction of $\Post$ over variables of 
  $\Leaves(Q)$). As $Q$ is FH-bisimilar to $Q'$ and $(\ostate{s_{1 i}^{i \in 
@@
  		\Pred\,'\subst{b_{j_0 x}\leftarrow v_x}\land\Pred_{OT_x},  
- 		\Post'\uplus \Post_{OT_x} }
+ 		\Post\,'\uplus \Post_{OT_x} }
  	{\ostate{s_{2 i }^{i\in L'\uplus L_Q}} \OTarrow {v_x}
@@
  	\land v_Q\!=\!v_x \land  
- 	\Pred_{tgt_x}\subst{\Post''}\subst{\Post_{OT_x}}\right)
+ 	\Pred_{tgt_x}\subst{\Post\,''}\subst{\Post_{OT_x}}\right)
  }
@@
  		\land v_Q\!=\!v_x \land  
- 		\Pred_{tgt_x}\subst{\Post''}\subst{\Post_{OT_x}}\right)
+ 		\Pred_{tgt_x}\subst{\Post\,''}\subst{\Post_{OT_x}}\right)
  	}
@@
  	\item Concerning the last term, we need 
- 	$\Pred_{tgt_x}\subst{\Post_{OT}}\subst{\Post'\uplus \Post_{OT_x}}$ 
+ 	$\Pred_{tgt_x}\subst{\Post_{OT}}\subst{\Post\,'\uplus \Post_{OT_x}}$ 
  	, i.e.:
- 	$\Pred_{tgt_x}\subst{\Post'\uplus 
- 		\Post''}\subst{\Post'\uplus \Post_{OT_x}}$. We 
+ 	$\Pred_{tgt_x}\subst{\Post\,'\uplus 
+ 		\Post\,''}\subst{\Post\,'\uplus \Post_{OT_x}}$. We 
  	can conclude by observing that	$\Pred_{tgt_x}$ does not use any variable of $P$ 
- 	and thus $\subst{Post'}$ has no effect.
+ 	and thus $\subst{Post\,'}$ has no effect.
  \end{itemize}	

### 2017-12-19 2016-Weak-FH-Bisim/WeakBisim.tex
New notation : Pred s,t in bisim and in proof

@@
   \hspace{0.5cm}
- \includegraphics[width=4.5cm]{XFIG/TransportSchema}
+ \includegraphics[width=4.5cm]{XFIG/TransportSpec}
   \caption{Schema and specification of the protocol }  \label{schema:enable-pnets}
@@
 %\begin{minipage}{6cm}
-  \includegraphics[width=10cm]{XFIG/ABPSchema}
+  \centerline{\includegraphics[width=11cm]{XFIG/ABPSchema}}
   \caption{Composed pNet with the ABP protocol}  \label{schema:enable-composed}
@@
       predicate $\Pred_{s,t}$.
-      \TODO{LudoPred -> Pred s,t}
  FH-bisimulation is defined formally: 
@@
 $\mathcal{R}$ is an FH-bisimulation iff for any  states
-$s\in\mathcal{S}_1$ and $t\in\mathcal{S}_2$, $(s,t|\Pred)\in\mathcal{R}$, we 
+$s\in\mathcal{S}_1$ and $t\in\mathcal{S}_2$, $(s,t|\Pred_{s,t})\in\mathcal{R}$, we 
 have
@@
  and  \\
- $\Pred \land \Pred_{OT}\\
+ $\Pred_{s,t} \land \Pred_{OT}\\
 \hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
@@
        	$\mathcal{T}_1$ and of  $\mathcal{T}_2$; members of $\mathcal{R}$ are of the form 
-       	$(s,t|\Pred)$.
+       	$(s,t|\Pred_{s,t})$.
        	Suppose we also  have $\mathcal{R}'$ an FH-bisimulation relation between states 
@@
        	form 
-       	$(t,u|\Pred\,')$.
+       	$(t,u|\Pred_{t,u})$.
 
@@
        	\[\mathcal{R}'' = 
-       	\{(s,u|\Pred\,'')\,\,\Big|\,\Pred\,''=\bigvee_{\begin{array}{c}       		
-       		(s,t|\Pred)\in\mathcal{R}\\ (t,u|\Pred\,')\in\mathcal{R}' 	
+       	\{(s,u|\Pred_{s,u})\,\,\Big|\,\Pred_{s,u}=\bigvee_{\begin{array}{c}       		
+       		(s,t|\Pred_{s,t})\in\mathcal{R}\\ (t,u|\Pred_{t,u})\in\mathcal{R}' 	
        		\end{array}
-       	}\,\Pred\land\Pred\,'\}\]
+       	}\,\Pred_{s,t}\land\Pred_{t,u}\}\]
 
@@
        	that $\mathcal{R}''$ is an FH-bisimulation. Consider 
-       	$(s,u|\Pred\,'')\in\mathcal{R}''$. Then there is a set of states of 
+       	$(s,u|\Pred_{s,u})\in\mathcal{R}''$. Then there is a set of states of 
        	$\mathcal{T}_2$ relating $s$ and $u$, let $(t_p)^{p\in P}$ be this family.  
-       	       	We have $\Pred\,'' = \bigvee_{p\in P} \Pred_p\land\Pred\,'_p$.
+       	       	We have $\Pred_{s,u} = \bigvee_{p\in P} \Pred_{s,p}\land\Pred_{p,u}$.
 
@@
        	For any $p\in P$ by definition of $\mathcal{R}''$,
-       	$(s,t_p|\Pred_p)\in\mathcal{R}$,  and 
-       	$(t_p,u|\Pred\,'_p)\in\mathcal{R}'$. 
+       	$(s,t_p|\Pred_{s,p})\in\mathcal{R}$,  and 
+       	$(t_p,u|\Pred\,'_{p,u})\in\mathcal{R}'$. 
        	We have 
@@
 
-       	$\Pred_p \land \Pred_{OT}\\
+       	$\Pred_{s,p} \land \Pred_{OT}\\
        	\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
@@
        	for any open transition $OT_{px}$, since
-       	$(t_p,u|\Pred\,^\prime_p)\in\mathcal{R}'$ there exist open transitions
+       	$(t_p,u|\Pred_{p,u})\in\mathcal{R}'$ there exist open transitions
        	$OT_{pxy}^{y\in Y} \subseteq \mathcal{T}_3$:
@@
        	(t_{px},u_{pxy}|\Pred_{{pxy}})\in \mathcal{R}'$; and  \\
-       	$\Pred\,'_p \land \Pred_{OT_{p x}}\\
+       	$\Pred_{p,u} \land \Pred_{OT_{p x}}\\
        	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
@@
        	More precisely, $t_{px} \in ({t_p}')^{p\in P'}$ where $({t_p}')^{p\in 
-       		P'}$ \TODO{Pas sure prime utile t, or p, or P}
+       		P'}$ \TODO{Pas sure prime utile t, or p, or P ; SI:  $P\neq P'$ et 
+       		les $t_p'$ sont pas les $t_p$}
        	is 
@@
 
-       	Second, by definition of bisimulation we need (recall that $\Pred\,''$ is the 
+       	Second, by definition of bisimulation we need (recall that $\Pred_{s,u}$ is the 
        	original predicate relating $s$ and $u$ by definition of the transitive 
@@
        	\begin{small}
-       		$\Pred\,'' \land \Pred_{OT}\\
+       		$\Pred_{s,u} \land \Pred_{OT}\\
        		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
@@
        	\begin{small}
-       		$\Pred_p \land \Pred_{OT}\land\Pred_p\!'\\
+       		$\Pred_{s,p} \land \Pred_{OT}\land\Pred_{p,u}\\
        		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
@@
        		\land v\!=\!v_{px} \land
-       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\land\Pred_p\!'\\
+       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\land\Pred_{p,u}\\
        		%
        		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-       		\left( \forall j. b_j=b_{jpx}  \Rightarrow (\Pred_{OT_{px}}\land\Pred_p\!')
+       		\left( \forall j. b_j=b_{jpx}  \Rightarrow (\Pred_{OT_{px}}\land\Pred_{p,u})
        		\land v\!=\!v_{px} \land
@@
 
-       	This allows us to conclude, with $\Pred\,'' = \bigvee_{p\in P} 
-       	\Pred_p\land\Pred_p\!'$:
+       	This allows us to conclude, with $\Pred_{s,u} = \bigvee_{p\in P} 
+       	\Pred_{s,p}\land\Pred_{p,u}$:
+
       	\begin{small}     	
-$\Pred\,'' \land \Pred_{OT}\\
+$\Pred_{s,u} \land \Pred_{OT}\\
 \hspace{1cm} \implies\!\!\! \bigvee_{p\in P} (
-\Pred_p\land\Pred_p\!' \land \Pred_{OT})\\
+	\Pred_{s,p}\land\Pred_{p,u} \land \Pred_{OT})\\
 \hspace{1cm} \implies\!\!\!\bigvee_{p\in P}
@@
 
+ \TODO{Ludo: switch the proof to new notations : s,t instead of 21 s2, and Pred s,t}
  Let $\Leaves(Q)=p_l^{l\in L}$, $\Leaves(Q')={p'}_l^{l\in L'}$, 

### 2017-12-21 2016-Weak-FH-Bisim/WeakBisim.tex
changed notations in proof of thm 4 (s,t, tgt)

@@
 
+\subsection{Composition Lemmas}       
        The proof of the other theorems rely on two main lemmas,
@@
 
-         \newpage
- \section{Proof of Theorem ~\ref{thm-congr-eq}}
+ \subsection{Proof of Theorem ~\ref{thm-congr-eq}}
  The proof of Theorem~\ref{thm-congr-eq} exhibits classically a bisimulation relation for 
@@
 
- \TODO{Ludo: switch the proof to new notations : s,t instead of 21 s2, and Pred s,t}
  Let $\Leaves(Q)=p_l^{l\in L}$, $\Leaves(Q')={p'}_l^{l\in L'}$, 
@@
  $\mathcal{R}$ that is an FH-bisimulation between the open automata of the two pNets. 
- We will consider the relation $\mathcal{R}'=\{(s_1,s_2|\Pred)|s_1=s'_1\uplus s \land 
- s_2=s'_2\uplus s \land s\in \mathcal{S}_P \land (s_1',s_2'|\Pred)\in\mathcal{R}\}$ 
+ We will consider the relation $\mathcal{R}'=\{(s,t|\Pred_{s,t})|s=s'\uplus s'' \land 
+ t=t'\uplus s'' \land s''\in \mathcal{S}_P \land (s',t'|\Pred_{s,t})\in\mathcal{R}\}$ 
  where $\mathcal{S}_S$ is the set of states of the open automaton of $P$.	We will prove 
  that $\mathcal{R}'$ is an open FH-bisimulation. Consider a pair of FH-bisimilar 
- states: $(\ostate{s_{1 i}^{i \in L_P\uplus L}},\ostate{{s}_{2 i}^{i \in L'}\uplus 
- 	{s}_{1 i}^{i \in L_P}}|\Pred)\in\mathcal{R}'$. %Those are states of the open 
+ states: $(\ostate{s_{i}^{i \in L_P\uplus L}},\ostate{{t}_{i}^{i \in L'}\uplus 
+ 	{s}_{i}^{i \in L_P}}|\Pred_{s,t})\in\mathcal{R}'$. %Those are states of the open 
  %	automata of 
@@
  	\{\xrightarrow{b_j}_j\}^{j\in J},\Pred_{OT},\Post_{OT}}
- { \ostate{s_{1 i}^{i \in L_P\uplus L}}\OTarrow {v} \ostate{{s'}_{1 i}^{i \in 
+ { \ostate{s_{i}^{i \in L_P\uplus L}}\OTarrow {v} \ostate{{s'}_{i}^{~i \in 
  			L_P\uplus 
@@
  		\Post'}
- 	{\ostate{s_{1 i}^{i\in L_P}} \OTarrow {v}
- 		\ostate{s_{1 i}'^{\, i\in L_P}}}
+ 	{\ostate{s_{i}^{i\in L_P}} \OTarrow {v}
+ 		\ostate{s_{i}'^{~ i\in L_P}}}
  }\\
@@
  		\Post''}
- 	{\ostate{s_{1 i}^{i\in L}} \OTarrow {v_Q}
- 		\ostate{s_{1 i}'^{\, i\in L}}}
+ 	{\ostate{s_{i}^{i\in L}} \OTarrow {v_Q}
+ 		\ostate{s_{i}'^{~ i\in L}}}
  }\end{mathpar}
@@
  \Post\,''$ ($\Post\,''$ is the restriction of $\Post$ over variables of 
- $\Leaves(Q)$). As $Q$ is FH-bisimilar to $Q'$ and $(\ostate{s_{1 i}^{i \in 
- 		L}},\ostate{{s}_{2 i}^{i \in L'}}|\Pred)\in\mathcal{R}$ there is a family 
+ $\Leaves(Q)$). As $Q$ is FH-bisimilar to $Q'$ and $(\ostate{s_{i}^{i \in 
+ 		L}},\ostate{{t}_{i}^{i \in L'}}|\Pred_{s,t})\in\mathcal{R}$ there is a family 
  $OT'_x$ 
@@
  Q'\models\inferrule*[myfraction=\reddottedrule]
- {\{s_{2 i}\xrightarrow{a_{i x}}_i s_{2 i x}\}^{i\in I_{x}},
+ {\{t_{i}\xrightarrow{a_{i x}}_i t_{i x}\}^{i\in I_{x}},
  	\{\xrightarrow{b_{j x}}_j\}^{j\in J\cap\Holes(Q)}, 
  	\Pred_{OT_x},\Post_{OT_x}}
- {\ostate{s_{2 i}^{i\in L'}} \OTarrow {v_x} \ostate{s_{2 i x}^{i\in L'}}}
+ {\ostate{t_{i}^{i\in L'}} \OTarrow {v_x} \ostate{t_{i x}^{i\in L'}}}
  \end{mathpar}
- and  $\forall x, (\ostate{s_{1 i}^{i\in L}},\ostate{s_{2 i x}^{i\in 
- 		L'}}|\Pred_{tgt_x})\in 
+ and  $\forall x, (\ostate{s_{i}^{i\in L}},\ostate{t_{i x}^{i\in 
+ 		L'}}|\Pred_{s x})\in 
  \mathcal{R}$; 
@@
  \land v_Q\!=\!v_x \land  
- \Pred_{tgt_x}\subst{\Post''}\subst{\Post_{OT_x}}\right)$
+ \Pred_{s x}\subst{\Post''}\subst{\Post_{OT_x}}\right)$
 
@@
  the transition of $P$ and obtain a new family $OT_x$ of open transitions (where for 
- $i\in L_P$, $s_{2 i}=s_{1 i}$ and $s_{2 i x}=s'_{1 i}$, and for $j\in Holes(P)$, 
+ $i\in L_P$, $t_{i}=s_{i}$ and $t_{i x}=s'_{i}$, and for $j\in Holes(P)$, 
  $b_{j x}=b_j$):\\[-2ex]
@@
  {\inferrule*[myfraction=\reddottedrule]
- 	{\{s_{2 i}\xrightarrow{a_{i x}}_i {s}_{2 i x}\}^{i\in I_x \uplus 
+ 	{\{t_{i}\xrightarrow{a_{i x}}_i {t}_{i x}\}^{i\in I_x \uplus 
  			(I\cap L_P)},
@@
  		\Post\,'\uplus \Post_{OT_x} }
- 	{\ostate{s_{2 i }^{i\in L'\uplus L_Q}} \OTarrow {v_x}
- 		\ostate{{s}_{2 i x}^{i\in L'\uplus L_Q}}}
+ 	{\ostate{t_{i }^{i\in L'\uplus L_Q}} \OTarrow {v_x}
+ 		\ostate{{t}_{i x}^{i\in L'\uplus L_Q}}}
  }
@@
  FH-bisimulation between $OT$ and $OT_x$.
- $\forall x, (\ostate{{s'}_{1 i}^{i\in L_P\uplus L}},\ostate{s_{2 i 
- 		x}^{i\in L_P\uplus L'}}|\Pred_{tgt_x})\in 
+ $\forall x, (\ostate{{s'}_{i}^{~i\in L_P\uplus L}},\ostate{t_{i 
+ 		x}^{i\in L_P\uplus L'}}|\Pred_{s x})\in 
  \mathcal{R}'$ (by definition of
@@
  \noindent                        
- \begin{small} $\Pred \land \Pred_{OT} \implies
- 	\Pred\land(\Pred\,'\land \Pred\,'')\subst{b_{j_0}\leftarrow v_Q}\\ % reversed 
+ \begin{small} $\Pred_{s,t} \land \Pred_{OT} \implies
+ 	\Pred_{s,t}\land(\Pred\,'\land \Pred\,'')\subst{b_{j_0}\leftarrow v_Q}\\ % reversed 
  	%substitution 
  	\implies 
- 	(\Pred\land\Pred\,'')\land \Pred\,'\subst{b_{j_0}\leftarrow v_Q}\\ % $b_{j_0}$ only 
+ 	(\Pred_{s,t}\land\Pred\,'')\land \Pred\,'\subst{b_{j_0}\leftarrow v_Q}\\ % $b_{j_0}$ 
+ 	%only 
  	%appears 
@@
  	\land v_Q\!=\!v_x \land  
- 	\Pred_{tgt_x}\subst{\Post\,''}\subst{\Post_{OT_x}}\right)
+ 	\Pred_{s x}\subst{\Post\,''}\subst{\Post_{OT_x}}\right)
  }
@@
  		\land v_Q\!=\!v_x \land  
- 		\Pred_{tgt_x}\subst{\Post\,''}\subst{\Post_{OT_x}}\right)
+ 		\Pred_{s x}\subst{\Post\,''}\subst{\Post_{OT_x}}\right)
  	}
@@
  	\item Concerning the last term, we need 
- 	$\Pred_{tgt_x}\subst{\Post_{OT}}\subst{\Post\,'\uplus \Post_{OT_x}}$ 
+ 	$\Pred_{s x}\subst{\Post_{OT}}\subst{\Post\,'\uplus \Post_{OT_x}}$ 
  	, i.e.:
- 	$\Pred_{tgt_x}\subst{\Post\,'\uplus 
+ 	$\Pred_{s x}\subst{\Post\,'\uplus 
  		\Post\,''}\subst{\Post\,'\uplus \Post_{OT_x}}$. We 
- 	can conclude by observing that	$\Pred_{tgt_x}$ does not use any variable of $P$ 
+ 	can conclude by observing that	$\Pred_{s x}$ does not use any variable of $P$ 
  	and thus $\subst{Post\,'}$ has no effect.
@@
 
-        \newpage
-        \section{Proof of Theorem ~\ref{thm-ctxt-eq}}
+        \subsection{Proof of Theorem ~\ref{thm-ctxt-eq}}
+ \TODO{Ludo: switch the proof to new notations : s,t instead of s1 s2, and Pred s,t}
 The proof of Theorem~\ref{thm-ctxt-eq} exhibits  a bisimulation relation for a 

### 2017-12-21 2016-Weak-FH-Bisim/WeakBisim.tex
changed notation in proof of thm 5 too

@@
         \subsection{Proof of Theorem ~\ref{thm-ctxt-eq}}
- \TODO{Ludo: switch the proof to new notations : s,t instead of s1 s2, and Pred s,t}
+
 The proof of Theorem~\ref{thm-ctxt-eq} exhibits  a bisimulation relation for a 
@@
 	$\mathcal{R}$ that is an FH-bisimulation between the open automata of the two pNets. 
-	We will consider the relation $\mathcal{R}'=\{(s_1,s_2|\Pred)|s_1=s'_1\uplus s \land 
-	s_2=s'_2\uplus s \land s\in \mathcal{S}_Q \land (s_1',s_2'|\Pred)\in\mathcal{R}\}$ 
+	We will consider the relation $\mathcal{R}'=\{(s,t|\Pred_{s,t})|s=s'\uplus s'' \land 
+	t=t'\uplus s'' \land s\in \mathcal{S}_Q \land (s',t'|\Pred_{s,t})\in\mathcal{R}\}$ 
 	where $\mathcal{S}_Q$ is the set of states of the open automaton of $Q$.	We will prove 
@@
 		\{\xrightarrow{b_j}_j\}^{j\in J},\Pred_{OT},\Post_{OT}}
-	{ \ostate{s_{1 i}^{i \in L\uplus L_Q}}\OTarrow {v} \ostate{{s'}_{1 i}^{i \in 
+	{ \ostate{s_{i}^{i \in L\uplus L_Q}}\OTarrow {v} \ostate{{s'}_{i}^{~i \in 
 	L\uplus 
@@
 					\Post'}
-				{\ostate{s_{1 i}^{i\in L}} \OTarrow {v}
-					\ostate{s_{1 i}'^{\, i\in L}}}
+				{\ostate{s_{1}^{i\in L}} \OTarrow {v}
+					\ostate{s_{i}'^{~ i\in L}}}
 			}\\
@@
 					\Post''}
-				{\ostate{s_{1 i}^{i\in L_Q}} \OTarrow {v_Q}
-					\ostate{s_{1 i}'^{\, i\in L_Q}}}
+				{\ostate{s_{i}^{i\in L_Q}} \OTarrow {v_Q}
+					\ostate{s_{i}'^{~ i\in L_Q}}}
 			}\end{mathpar}
@@
 			\Post''$ ($\Post''$ is the restriction of $\Post$ over variables of 
-			$\Leaves(Q)$). As $P$ is FH-bisimilar to $P'$ and $(\ostate{s_{1 i}^{i \in 
-			L}},\ostate{{s}_{2 i}^{i \in L'}}|\Pred)\in\mathcal{R}$ there is a family 
+			$\Leaves(Q)$). As $P$ is FH-bisimilar to $P'$ and $(\ostate{s_{i}^{i \in 
+			L}},\ostate{{t}_{i}^{i \in L'}}|\Pred_{s,t})\in\mathcal{R}$ there is a family 
 			$OT'_x$ 
@@
 			P'\models\inferrule*[myfraction=\reddottedrule]
-			{\{s_{2 i}\xrightarrow{a_{i x}}_i s_{2 i x}\}^{i\in I_{x}},
+			{\{t_{i}\xrightarrow{a_{i x}}_i t_{i x}\}^{i\in I_{x}},
 				\{\xrightarrow{b_{j x}}_j\}^{j\in J'}, 
 				\Pred_{OT_x},\Post_{OT_x}}
-			{\ostate{s_{2 i}^{i\in L'}} \OTarrow {v_x} \ostate{s_{2 i x}^{i\in L'}}}
+			{\ostate{t_{i}^{i\in L'}} \OTarrow {v_x} \ostate{t_{i x}^{i\in L'}}}
 			%         \right)
 			\end{mathpar}
-			and  $\forall x, (\ostate{s_{1 i}^{i\in L}},\ostate{s_{2 i x}^{i\in 
-			L'}}|\Pred_{tgt_x})\in 
+			and  $\forall x, (\ostate{s_{i}^{i\in L}},\ostate{t_{i x}^{i\in 
+			L'}}|\Pred_{s x})\in 
 			\mathcal{R}$; 
 			and  \\
-			$\Pred \land \Pred'
+			$\Pred_{s,t} \land \Pred\,'
 		 \Rightarrow \bigvee_{x\in X}
@@
 			\land v\!=\!v_x \land  
-			\Pred_{tgt_x}\subst{\Post'}\subst{\Post_{OT_x}}\right)$
+			\Pred_{s x}\subst{\Post'}\subst{\Post_{OT_x}}\right)$
 			%     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x}) \right)$.
@@
 			the transition of $Q$ and obtain a new family $OT_x$ of open transitions (where for 
-			$i\in L_Q$, $s_{2 i}=s_{1 i}$ and $s_{2 i x}=s'_{1 i}$, and for $j\in Holes(Q)$, 
+			$i\in L_Q$, $t_{i}=s_{i}$ and $t_{i x}=s'_{i}$, and for $j\in Holes(Q)$, 
 			$b_{j x}=b_j$):\\[-2ex]
@@
 				{\inferrule*[myfraction=\reddottedrule]
-					{\{s_{2 i}\xrightarrow{a_{i x}}_i {s}_{2 i x}\}^{i\in I_x \uplus 
+					{\{t_{i}\xrightarrow{a_{i x}}_i {t}_{i x}\}^{i\in I_x \uplus 
 					(I\cap L_Q)},
@@
 						\Post_{OT_x}\uplus \Post''}
-					{\ostate{s_{2 i }^{i\in L'\uplus L_Q}} \OTarrow {v_x}
-						\ostate{{s}_{2 i x}^{i\in L'\uplus L_Q}}}
+					{\ostate{t_{ i }^{i\in L'\uplus L_Q}} \OTarrow {v_x}
+						\ostate{{t}_{ i x}^{i\in L'\uplus L_Q}}}
 				}
@@
 			FH-bisimulation between $OT$ and $OT_x$.
-			 $\forall x, (\ostate{{s'}_{1 i}^{i\in L\uplus L_Q}},\ostate{s_{2 i 
-			x}^{i\in L'\uplus L_Q}}|\Pred_{tgt_x})\in 
+
+			 $\forall x, (\ostate{{s'}_{i}^{~i\in L\uplus L_Q}},\ostate{t_{i 
+			x}^{~i\in L'\uplus L_Q}}|\Pred_{s x})\in 
 			\mathcal{R}'$ (by definition of
@@
 \noindent                        
-\begin{small} $\Pred \land \Pred_{OT} \implies
- \Pred\land(\Pred\,'\land \Pred\,'')\subst{b_{j_0}\leftarrow v_Q}\\ % reversed 
+\begin{small} $\Pred_{s,t} \land \Pred_{OT} \implies
+ \Pred_{s,t}\land(\Pred\,'\land \Pred\,'')\subst{b_{j_0}\leftarrow v_Q}\\ % reversed 
  %substitution 
  \implies 
- (\Pred\land\Pred')\subst{b_{j_0}\leftarrow v_Q}\land \Pred\,''\\ % $b_{j_0}$ only 
+ (\Pred\land\Pred\,')\subst{b_{j_0}\leftarrow v_Q}\land \Pred\,''\\ % $b_{j_0}$ only 
  %appears 
@@
 \land v\!=\!v_x}} %\\ \hspace*{40mm} %
-\land \Pred_{tgt_x}\subst{\Post'}\subst{\Post_{OT_x}}) \land
-\Pred''\\ % 
+\land \Pred_{s x}\subst{\Post'}\subst{\Post_{OT_x}}) \land
+\Pred\,''\\ % 
 			%FH for P
@@
 \!\land\! v\!=\!v_x \!\land\!  
-\Pred_{tgt_x}\subst{\Post'}\subst{\Post_{OT_x}})}} 			
+\Pred_{s x}\subst{\Post'}\subst{\Post_{OT_x}})}} 			
 $\end{small}
@@
 	change the validity of the formula (those variables are not used).
-	\item We need $\Pred_{tgt_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}\uplus \Post''}$ 
+	\item We need $\Pred_{s x}\subst{\Post_{OT}}\subst{\Post_{OT_x}\uplus \Post''}$ 
 	, i.e.:
-	$\Pred_{tgt_x}\subst{Post'\uplus Post''}\subst{\Post_{OT_x}\uplus \Post''}$. We 
-	can conclude by observing that	$\Pred_{tgt_x}$ does not use any variable of $Q$ 
-	and thus $\subst{Post''}$ has no effect.
+	$\Pred_{s x}\subst{\Post'\uplus \Post''}\subst{\Post_{OT_x}\uplus \Post''}$. We 
+	can conclude by observing that	$\Pred_{s x}$ does not use any variable of $Q$ 
+	and thus $\subst{\Post''}$ has no effect.
 \end{itemize}	

### 2018-01-09 2017-Xudong-SMT/FM-2018-extended.tex
Version initiale pour soumission FM-extended

--- 2017-06-23 2017-Xudong-SMT/submit-ICTAC2017.tex
@@
 \begin{abstract}
-  %% \TODO{not good for a conference, (to be rewriten by Eric)}
-  %% We implement the symbolic semantics of open pNets using their
-  %% so-called ``Open Automaton'' behavioral semantics. This involve
-  %% building predicates expressing the synchronization conditions
-  %% allowing some combination of events in the pNet system. These
-  %% predicates are typically built using first order logic, plus some
-  %% predicates specific of particular action algebras. To reduce the
-  %% complexity of the generated open automata, we use the Z3 SMT engine
-  %% to check satisfiability of the predicates, and prune the state
-  %% space..
+  \TODO{not good for a FM, (to be rewriten by Eric)}
 
@@
     generated by the algorithm.
-\item We validate the whole approach on small use-cases covering all
-      important features of the model.
+  \item \ERIC{We show the interest of this approach on an
+    industrial-inspired use-case, namely one architectural pattern
+    extracted from the BIP specification of a nano satellite on-bord
+    software.} 
 \end{itemize}
@@
 
-% \TODO{I have removed some of the technical stuff, adding referemces to Forte'16.
-%  We will see if this is enough, and will have to check if this is coherent, and if we can remove more, but for ICTAC, we MUST keep enough formal stuff}
+\TODO{To be reduced, moving more material to the appendix}
 
@@
 
-%% \TODO{[We haven't used the input variables in this paper, we can remove them.]: NO, first see what we use to explain CCS use-case, then leave only a short definition of what we need}
-%% \QIN{[To be able to reason about the data flow between pLTSs, we
-%% distinguish \emph{input variables} of the form $?x$ within terms; the function
-%% $\vars(t)$ identifies the set of variables in a term
-%% $t\in\AlgT$, and $iv(t)$ returns its input variables.]}
-
 pNets can encode naturally the notion of input actions as found e.g. in value-passing CCS
@@
 communications.
-%\TODO{I removed the CCS input action stuff, check later if we need to
-%  replace it here by something different about input action notation}.
-
-%% Formally, value-passing actions \emph{\`a la} CCS, denoted as
-%% ``?ch(x)'' and ``!ch(exp)'' in our CCS running example, stand
-%% respectively for $CCSact(i(ch),?x)$ and $CCSact(ch,exp)$, where $ch$
-%% is a variable denoting a channel name, $?x$ is an input variable
-%% denoting the data argument received as input on $ch$, and $exp$ some
-%% data expression (containing no input variables). In our example we
-%% will use the usual CCS syntax. 
-%% %For Lotos-style
-%% %distributed synchronization, we use synchronization vectors that encode matching data
-%% %offers on a common gate; or 
-%% We can also use more complex action structure such as Meije-SCCS action
-%% monoids, like in $a.b$, $a^{f(n)}$ (see \cite{deSimone85}). The expressiveness of the synchronization constructs
-%% will depend on the action algebra.
 
@@
 $s_0 \in S$ is the initial state.
-%\item[$\bullet$]
- %Variables in
-%$\iv(\alpha)$ are assigned by the action, other variables can be assigned
-%by the additional assignments.
 \item[$\bullet$] $\to \subseteq S \times L \times S$ is the transition relation and 
@@
 If 
-%% $s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
-%% 		J}\rangle} s'\in \to $ then $\iv(\alpha)\!\subseteq\! \vars(s')$, 
-%% 		$\vars(\alpha)\backslash \iv(\alpha)\!\subseteq\! \vars(s)$, 
-%% 		$\vars(e_b)\!\subseteq\! \vars(s')$, and
-%% 		$\forall j\!\in\! J .\,\vars(e_j)\!\subseteq\! \vars(s)\land 
-%% x_j\!\in\!\vars(s')$.
-
 $s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
@@
 x_j\!\in\!\vars(s')$.
-
-%,  and $s= s'\Rightarrow J=\emptyset$. 
 \item[$\bullet$]
@@
 exposes a single resulting global action.
-% Actions involved at the pNet level (in the synchronization vectors) do
-% not need to distinguish between input and output
-% variables.
-%Action terms for pNets are defined as follows:
-%\[\begin{array}[l]{rcl@{\quad}l}
-%  \alpha\in \AlgAS &::=&a(Expr_1,\ldots,Expr_n)
-%\end{array}
-%\]
 
@@
 \item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets.
-%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which sub-pNets are indexed.
 
@@
 
-\section{Running Example}
-\label{section:examples}
+\section{BIP architectures, and their encodings into pNets}
+\label{section:BIParchitectures}
+
+\section{Running example}
+\label{section:FailureTimerMax}
 
@@
  \begin{figure}[t]
-   \centerline{\includegraphics[width=10cm]{XFIG/LOTOSFormula.eps}}
-   \caption{pNet encodings for the LOTOS expression}  \label{schema:lotos-pnet}
+   \centerline{\includegraphics[width=12cm]{XFIG/BIPspec-ArchFailureTimerMax}}
+   \caption{FailureTimer Architecture in BIP graphical syntax}  \label{schema:BIParchitecture}
  \end{figure}
 
-We use an example inspired from LOTOS, to illustrate
-the main features of pNets and our semantic construction algorithm.
-%% \QIN{
-%% Meanwhile, 
-%% the formula using operators from CCS can also be encoded into a pNet and 
-%% conducted with the same things.
-%% }
-%% \subsection{LOTOS Formula Example}
-We choose here the expression \texttt{P>>(acc(v);Q)}, that includes the
-Enable and Prefix 
-operators of the LOTOS language. For the readers not familiar with
-Lotos, the pNet encodings here should be sufficient to understand the
-Enable operator semantics.
-In Fig.~\ref{schema:lotos-pnet}, we show the encoding of the formula using pNets. 
-This pNet is composed of: a toplevel node PN1 encoding the Enable
-operator, a pLTS C1 acting as the {\sl controller} of the node; a hole
-representing the 
-process variable P; another node PN2 representing the Prefix
-operator, with its controller C2, and its hole Q.
-
-In order to show all features of the pNet model, we choose to use two
-styles of encodings in the controllers.
-% The most common style used in process calculi is ``state oriented'',
-Controller C2 is ``state oriented'': it has two states to
-indicate the position of the control point in the
-Prefix expression $(acc(v);Q)$. The second one is
-``data oriented'': controller C1 has a single state, with a state
-variable $s_0$ encoding the change of control point from the left to
-the right subnet.
-%% The transitions in the pLTS have the more general syntax:
-%% ``<action-expr> [guard] {sequence of assignments}''. Guards and
-%% assignments can only use the values of variables of their source state
-%% and values from input variables in the action expression; and a
-%% transition can only assign variables of its target state.
-
-The root pNet node PN1 has 3 sub-pNets: its controller C1,
-the hole P and the sub-pNet PN2.
-Three synchronization vectors define the possible
-synchronizations between the actions of the subnets.
-The first vector ``$< l, a_1 , \_ > -> a_1$'' transmits an action
-$a_1$ of P to the upper level. Here the ``l'' action is related
-to the corresponding transition of the controller C1, ``$\_$'' means
-that the corresponding subnet is not involved in this synchronization,
-and there is a guard meaning this synchronisation can only occur if
-$a_1$ is not a $\delta$.
-The second synchronisation vector composes an
-action $\delta(x)$ from $P$ with an $acc(x)$ from $Q$, transmitting a
-value $x$ before $Q$ takes the control; 
-The vector result $\underline{\delta(x)}$ is a ``synchronized''
-action, that cannot be further
-synchronized at upper levels. Synchronized actions is a useful
-generalization of the notion of internal actions, that will be
-convenient for observing internal events during model-checking.
-% The last vector acts is to the first one.  
-% Similarly the node PN2 has two synchronization vectors to encode
-% the behavior of the Prefix operator.
-
-It should be easy to see that this pNet system encodes properly the
-behavioral semantics of the corresponding algebra expression. We remark
-that it is built in a systematic structural way, one pNet node
-encoding each operator.
-%% It is parameterized both at the level of
-%% actions variables (occurring within the controllers and the
-%% synchronization vectors), and at the level of process parameters
-%% (holes).
-
-%% \TODO{I'm thinking about moving this second example to section 5...}
-%% \QIN{[This CCS example is removed.]}
-
-%\subsection{CCS Parallel Example}
-%
-%\begin{figure}[h]
-%  \centerline{\includegraphics[width=10cm]{XFIG/CCS1.eps}}
-%  \caption{pNet encodings for the CCS expression}  \label{schema:ccs-pnet}
-%\end{figure}
-%
-%\QIN{
-%This CCS expression composing two operators, parallel and prefix. In Fig.~\ref{schema:ccs-pnet}, 
-%it is easy to recognize that the pNets $PN2$ and $PN3$ are similar to 
-%the sub-pNet in the LOTOS example in their structure and synchronization vectors. 
-%That is because they are the operators conduct a similar behavior from different algebras.
-%}
-%
-%\QIN{
-%To present the parallel property, we have defined a set of synchronization vectors composing 
-%two subnets. We use the notation from the CCS to present the emit and receive action. 
-%The variables $v_1$, $v_2$ are the data transmitting between two components, 
-%showing its value-passing behavior.
-%}
+\begin{figure}[t]
+   \centerline{\includegraphics[width=12cm]{XFIG/BIPpnet-ArchFailureTimerMax}}
+   \caption{FailureTimer pNet encoding}  \label{schema:BIParchitecture}
+ \end{figure}
 
@@
 
+\begin{figure}[t]
+   \centerline{\includegraphics[width=12cm]{XFIG/BIPresult-ArchFailureTimerMax}}
+   \caption{Open Automaton\TODO{syntax could be better...}}  \label{schema:resultOA}
+ \end{figure}
+
 \begin{figure}[h]
-  \centerline{\includegraphics[width=5cm]{XFIG/LOTOSresult}}
+%  \centerline{\includegraphics[width=5cm]{XFIG/LOTOSresult}}
 

### 2018-01-09 2017-Xudong-SMT/FM-2018-extended.tex
appendix

@@
 
+\TODO{Improve this, inserting the main definition from the ``Checker'' document}
 %% Open pNet framework provides us
@@
 \paragraph{Translation of Action algebra presentation}
-
+\TODO{Exerpt of the formalisation}
 The $datatypes$ are declared according to the $sorts$ the users
@@
 \paragraph{Translating assignments into predicate terms}
+\TODO{Exerpt of the formalisation}
 
@@
 \label{section:full-result}
-% \TODO{
-% Xudong: full result of the tool execution on the running example\\\\
-% Open Automata of the CCS example.
-
-% \QIN{[The fig is improved. A little change on the comments.]}
-
-% \subsubsection{Result of LOTOS example}
-
+
+\TODO{Update: we have 11 satisfiable OTs here}
 Our tool builds 30 open
@@
 %  \centerline{\includegraphics[width=5cm]{XFIG/LOTOSresult}}
+  \TODO{Detaisl of some OTs of the FailureTimer}
 
@@
     {\ostate{00} \xrightarrow{v_2} \ostate{01}}\\
-  \end{array}$
-
-  $\begin{array}{@{}r@{}l@{}}
-    ot_3  = &\openrule{\{0 \xrightarrow{r}_{C_1} 0, 1 \xrightarrow{q}_{C_2} 1\}, ~~\{\xrightarrow{hb_{3}}_Q\}, ~~[s_0=1 \!\land\! hb_{3} \neq acc(x) \!\land\! v_3=hb_{3}]}
-    {\ostate{01} \xrightarrow{v_3} \ostate{01}}\\
   \end{array}$
@@
 
+\TODO{Change perspective: we are working on the formal extensino of
+  BIB architectures, and their semantics in terms of pNets. Then
+  bisimulation and model-checking principles adapted to open pNet
+  systems are under development}
+
 Naturally, our next goals after the generation of the open automata
@@
 % \newpage
-% \appendix
+\appendix
+
+\section{More details on the generation algorithm}
+\subsection{Algebra specification}
+\subsection{Term algebra: type system and static semantics}
+\subsection{Variable managment}
+\subsection{Filtering the behaviour combinations}
+\subsection{Translation to SMTlib input language}
+\subsection{Elimination of intermediate variables}
+
+\section{Full examples}
+\TODO{May be we use two architecture examples here, a simpler one,
+  before the Failure Timer ?}
+\subsection{A very simple architecture}
+\subsection{Full input for the FailureTimer architecture}
+\subsection{Full output for the FailureTimer open automaton}
+\subsection{Scaling up: several subsystems on the same bus}
 

### 2018-01-11 2016-Weak-FH-Bisim/WeakBisim.tex
small modifs

@@
 
-\RAB{La notation overline n'a pas ete introduite auparavant? Aussi, je n'ai pas trop bien 
-saisi quand on utilise overline et la la notation k in K}\LUDO{DONE}
-
 A pNet $Q$ is \emph{closed} if it has no hole: $\Holes(Q)=\emptyset$; else it
@@
 \end{figure}
-
-\RAB{les notations des figures pretes a confusion: carre/carre arrondi et rond/triangle plein}
 
@@
 the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
-\[\Pred_{\symb{sv}}(SV_k, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow
+\[\Pred_{\symb{sv}}(SV_k, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow \bigg(
 \begin{array}{l}
@@
 \forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v'
-\end{array}\]
+\end{array} \bigg)\]
 
@@
        	and $(t_{px},u_{pxy}|\Pred_{{pxy}})\in \mathcal{R}'$. 
-       	More precisely, $t_{px} \in ({t_p}')^{p\in P'}$ where $({t_p}')^{p\in 
+       	More precisely, $t_{px} \in ({t'_p})^{p\in P'}$ where $({t'_p})^{p\in 
        		P'}$ \TODO{Pas sure prime utile t, or p, or P ; SI:  $P\neq P'$ et 

### 2018-01-12 2017-Xudong-SMT/FM-2018-extended.tex
Merge documents.
Add the section 6.4 from "checker".
Add the section 6.5 from "elim_var"(never commited to GitHub).

@@
 \usepackage{amsmath,amssymb,amscd,mathrsfs}
+% \usepackage{array,booktabs,arydshln,xcolor}
+\usepackage{array,booktabs,xcolor}
 \DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
@@
 \algnewcommand{\IfThenElse}[3]{\State \algorithmicif\ #1\ \algorithmicthen\ #2\ \algorithmicelse\ #3}% \IfThenElse{<if>}{<then>}{<else>}
+%\DeclareMathOperator{\card}{card}
+%\DeclareMathOperator{\Flat}{Flat}
+\renewcommand{\P}{\mathcal P}
+\usepackage{listings}
+\lstset{basicstyle=\small}
+%\usepackage{algorithm} 
+%\usepackage{algpseudocode}
 
@@
 
+%\begin{algorithm}
+%\caption{Open Automaton Generation}
+%\begin{algorithmic}[1]
+%
+%\State Initialize sets $U$, $E$ for unexplored/explored global states
+%$U$, $L$ for result OTs;
+%\While{!isEmpty(U)}
+%	\State Chose a global state $S$ in $U$; recursively applying Tr1 or Tr2 on the root node;
+%	\If{Subnet is a pLTS}
+%                \State Get the local state of the pLTS $s$ from $S$;
+%		\For{each transition $tr$ starting from $s$} Apply Tr1
+%			\State Build the corresponding
+%                        $OT$; store $OT$ in $L$; 
+%                 \EndFor
+%	\EndIf
+%	\If{Subnet is a pNet}
+%		\For{each $sv \in SV$} Apply Tr2
+%			\State Invoke $Combining()$ to generate the
+%                        combination of sub-transitions, $Matching()$
+%                        to match the combination with the $sv$; Store the result OTs in $L$; 
+%		\EndFor
+%	\EndIf
+%	\For{each target global state $T$ from $OT \in L$}
+%		\IfThen{$(!U.contains(T))\ \&\&\ (!E.contains(T))$}{Add $T$ into the $U$;}
+%	\EndFor
+%\EndWhile
+%\State Prune the open transitions in $L$ using the SMT solver;
+%\State \Return $L$;
+%
+%\end{algorithmic}  
+%\end{algorithm}
+
 \begin{algorithm}
@@
 \begin{algorithmic}[1]
-
-\State Initialize sets $U$, $E$ for unexplored/explored global states
-$U$, $L$ for result OTs;
+\Require The pNet node P.
+\State Initialize sets $U$, $E$ for unexplored/explored global states, $L$ for result OTs;
 \While{!isEmpty(U)}
-	\State Chose a global state $S$ in $U$; recursively applying Tr1 or Tr2 on the root node;
-	\If{Subnet is a pLTS}
-                \State Get the local state of the pLTS $s$ from $S$;
-		\For{each transition $tr$ starting from $s$} Apply Tr1
-			\State Build the corresponding
-                        $OT$; store $OT$ in $L$; 
-                 \EndFor
-	\EndIf
-	\If{Subnet is a pNet}
-		\For{each $sv \in SV$} Apply Tr2
-			\State Invoke $Combining()$ to generate the
-                        combination of sub-transitions, $Matching()$
-                        to match the combination with the $sv$; Store the result OTs in $L$; 
-		\EndFor
-	\EndIf
+	\State Chose $S$ in $U$;
+	\State OT = MakeTransitions(P, S);
+        \State Store $OT$ in $L$; 
 	\For{each target global state $T$ from $OT \in L$}
@@
 
-Algorithm 1 shows the main structure of the algorithm: 
-the computation repeats applying Tr1 and Tr2 to build all possible
-combinations of behaviors of pLTS and Holes, through all possible
-synchronisation vectors. The resulting open transitions are checked
-for satisfiability by the SMT solver.
+\begin{algorithm}
+\caption{MakeTransitions()}
+\begin{algorithmic}[1]
+\Require The pNet node P; The start global state S.
+\State Initialize a list $l$, $L$ for sub-transitions/transitions.
+	\For{each Subnet in P}
+	\\ ~~~ $\setminus \setminus$ Recursively applying Tr1 or Tr2 on the sub-nodes.
+                \State Store MakeTransitions(Subnet, S) in $l$;
+	\EndFor
+	\For{each $sv \in SV$}
+		\State $comb = Combining(l)$;
+                 \State $ot = Matching(sv, comb, hole, v)$;
+                 \State Store $ot$ in $L$; 
+	\EndFor
+\State \Return $L$;
+\end{algorithmic}  
+\end{algorithm}
+
+\subsection{The Generation of Open Automata}
+
+\QIN{
+We have already have the sketch of computing the open automata \cite{???}.
+While in our implementation we does not build explicitly a proof tree for every open transition.
+Instead, we repeat applying the Tr1 or Tr2 to generate the sub-transitions.
+Tr1 is applied on the leaf (pLTS) simply take the pLTS transitions through the given start state and add the predicate in pNet to generate the open transition.
+When applying Tr2 we use two methods, combining and matching, to generate the new predicate of the open transitions in a hierarchical manner
+as in this case the composition the subnets brings more constraints for synchronizing behaviors. 
+Beside the new generated predicate, the predicates from the subnets are also added as a conjunction with those new predicates.
+}
+
+%Algorithm 1 shows the main structure of the algorithm: 
+%the computation repeats applying Tr1 and Tr2 to build all possible
+%combinations of behaviors of pLTS and Holes, through all possible
+%synchronisation vectors. The resulting open transitions are checked
+%for satisfiability by the SMT solver.
 
@@
 %\paragraph{Combining and Matching using TR2}
-Our implementation does not build explicitly the proof trees for each
-open transition, but instead : [Combining] enumerate all possible combinations of
-pLTS transition (using TR1) and each synchronization vector choice
-(TR2); [Matching] build the corresponding transition, and in particular
-its predicate, in a hierarchical manner.
-Each time we apply Tr2, we build a predicate as a conjunction of two
-parts. The first part, which is the simpler one, composes the
-predicate from the 
-subnets and the guard from transitions in sub-pLTS or synchronization
-vectors. The second part is the conjunction of equations generated
-during matching the subnets' behaviors with the synchronization
-vectors.
+%Our implementation does not build explicitly the proof trees for each
+%open transition, but instead : [Combining] enumerate all possible combinations of
+%pLTS transition (using TR1) and each synchronization vector choice
+%(TR2); [Matching] build the corresponding transition, and in particular
+%its predicate, in a hierarchical manner.
+%Each time we apply Tr2, we build a predicate as a conjunction of two
+%parts. The first part, which is the simpler one, composes the
+%predicate from the 
+%subnets and the guard from transitions in sub-pLTS or synchronization
+%vectors. The second part is the conjunction of equations generated
+%during matching the subnets' behaviors with the synchronization
+%vectors.
 
@@
 
-\begin{algorithm}
-\caption{Combining}
-\begin{algorithmic}[1]
-
-%\Require The list $TR$ of the open transition sets of the subnets. 
-%\Ensure The list of all the possible combinations of open transitions $L_C$.
-\State Initialize an empty combination list $L_C$;
-\State Extract a list of open transitions $L_{ot}$ from $TR$;
-\State Add $null$ to $L_{ot}$;
-\State Get the combinations $L'_C$ of the $TR$;
-\For{each $ot \in L_{ot}$}
-	\For{each $C' \in L'_C$}
-		\State Add $ot$ into $C'$ to get a new tuple $C$;
-		\State Add $C$ into $L_C$;
-	\EndFor
-\EndFor 
-\State \Return $L_C$;
-
-\end{algorithmic}  
-\end{algorithm}
+%\begin{algorithm}
+%\caption{Combining}
+%\begin{algorithmic}[1]
+%
+%%\Require The list $TR$ of the open transition sets of the subnets. 
+%%\Ensure The list of all the possible combinations of open transitions $L_C$.
+%\State Initialize an empty combination list $L_C$;
+%\State Extract a list of open transitions $L_{ot}$ from $TR$;
+%\State Add $null$ to $L_{ot}$;
+%\State Get the combinations $L'_C$ of the $TR$;
+%\For{each $ot \in L_{ot}$}
+%	\For{each $C' \in L'_C$}
+%		\State Add $ot$ into $C'$ to get a new tuple $C$;
+%		\State Add $C$ into $L_C$;
+%	\EndFor
+%\EndFor 
+%\State \Return $L_C$;
+%
+%\end{algorithmic}  
+%\end{algorithm}
 
 \paragraph{Combining:}
-Algorithm 2 shows the combining algorithm for enumerating all possible
-working status combinations from subnets. Dealing with a list $TR$
-containing  sets of open transitions from different subnets,
-the algorithm choses one of sets $L_{ot}$ and does combining on the
-remaining part of $TR$ recursively. The case when a subnet is not working is
-managed by adding a $null$ into the $L_{ot}$.
+\QIN{
+The combining method enumerate all the possible status of the subnets.
+The result of the method hence call the combination as it present as all the possible combinations of their open transitions.
+Assume that there is a collection of $n$ subnets $L = {s_1, s_2, ..., s_n}$, if we notate $ot$ to be the set of open transitions of the subnet $s$ and $\eta$ means the subnet is not involved. 
+Then the combination $\texttt{COMB}$, a set of n-tuples, can be computed as an outer product of sets : 
+\[\texttt{COMB} : (\eta\cup ot_1) \times (\eta\cup ot_2)\times ... \times (\eta\cup ot_n) .\]
+}
+%Algorithm 2 shows the combining algorithm for enumerating all possible
+%working status combinations from subnets. Dealing with a list $TR$
+%containing  sets of open transitions from different subnets,
+%the algorithm choses one of sets $L_{ot}$ and does combining on the
+%remaining part of $TR$ recursively. The case when a subnet is not working is
+%managed by adding a $null$ into the $L_{ot}$.
 
@@
 
-\begin{algorithm}
-\caption{Matching}
-\begin{algorithmic}[1]
-
-%\Require 
-%The combination of subnets' open transitions $L_C$;
-%The behaviors of the holes $B$;
-%The set of synchronization vectors $SV$.
-%\Ensure 
-%The list of all the possible open transitions generated $L_{ot}$.
-\State Initial an empty result list $L_{ot}$;
-\For{each $C \in L_C$}
-	\For{each $sv \in SV$}
-		\State Clone the $sv$, the result is $sv'$;
-		\State Generate the fresh result action $ra$;
-		\State Combine $C, B, ra$ as a new vector $v$;
-		\For{each $(e_1 \in v )\&\& (e_2 \in sv')$}
-			\If{$(e_1\ is\ null\ \&\&\ e_2\ is\ not\ null)\ ||\ (e_1\ is\ not\ null\ \&\&\ e_2\ is\ null)$} 
-			\State Skip;
-			\Else ~ Add $(e_1 = e_2)$ into the $Pred$;
-			\EndIf
-		\EndFor
-		\State Generate the result open transition $ot$ with $Pred$;
-		\State Add the $ot$ into $L_{ot}$;
-	\EndFor
-\EndFor 
-\State \Return $L_{ot}$;
-
-\end{algorithmic} 
-\end{algorithm}
-
-\paragraph{Matching:} Algorithm 3 shows the algorithm matches
-combination $L_C$, hole behaviors $B$ with synchronization vectors
-$SV$ according to the definition of the predicate declared before. We
-clone the $sv$ using the fresh function to generate a new $sv'$ with
-fresh variables.The mismatch on working status is easy to detect so we
-filter them in the algorithm through checking the matching elements
-$e_1$ and $e_2$. 
-Then we build the resulting open transition. Satisfiability of the
-predicate is not checked at this level, but only later, at the
-toplevel of the pNet.
-
-\subsection{Fresh variables}
-
-%The variables in each synchronization vector are considered local, so
-%does the variables of an open transition such as its hole behaviors
-%and its result action. So we want rename the variables to make them
-%unique on every occurrence of a vector. Similarly, the name given to
-%the hole behaviors for each hole or the result action for each open
-%transition must be distinct. At the same time, we also hope them still
-%readable. Here we rename the variables with a regular format using the fresh function.
-
-Application of the semantic rules require generating a lot of fresh
-names, for different kind of variables. We could use a global name
-generator to guarantee unicity, but 
-at the same time, we also hope them still
-readable. Here we rename the variables with a regular format using the fresh function.
-More precisely, the fresh function generates a new name adding a
-suffix after the original name. The suffix contains three parts
-combined by a colon.
-
-\begin{definition}[Fresh variable]\label{fresh-variable}
-The format of \emph{fresh variable} (renaming) is defined as:
-``$\emph{prefix : tree\ index\ :\ counter}$''.
-\begin{itemize}
-   \item[$\bullet$] $prefix$ identifies the kind of the
-     variable. current kinds are: sva (SV action), ra (result action), hb (hole behavior).
-   \item[$\bullet$] $tree\ index$ is the index of the node containing the variable in the tree-like structure of the pNet.
-   \item[$\bullet$] $counter$ is the current value of the corresponding counter.
-\end{itemize}
-\end{definition}
-
-%\TODO{Option: Add the process and the vector ids ?}
-
-%$Prefix$ avoids the confusion between variables from different structures with the same name by attaching the type of the structure.
-$Tree\ index$ is given to every node of the pNets to mention which node the variable belongs to as pNets has a tree-like structure.
-To each node, the tree index is always a number sequence of the tree index of its higher level and the index of the node in this level at the last.
-$A\ set\ of\ counters$ is used to count the current times the SV, Hole, subnet invoked, or the number of possible OT generated to provide an identity.
-
-For example, in the running example, the first possible behavior of
-the hole, it doesn't have a name, only have the prefix ``hb''. The
-hole is the second subnets of the root node so its ``tree index'' is
-``12''. The fresh variable name is ``$\OTvar{:hb:12:1}$''.
+%\begin{algorithm}
+%\caption{Matching}
+%\begin{algorithmic}[1]
+%%\Require 
+%%The combination of subnets' open transitions $L_C$;
+%%The behaviors of the holes $B$;
+%%The set of synchronization vectors $SV$.
+%%\Ensure 
+%%The list of all the possible open transitions generated $L_{ot}$.
+%\State Initial an empty result list $L_{ot}$;
+%\For{each $C \in L_C$}
+%	\For{each $sv \in SV$}
+%		\State Clone the $sv$, the result is $sv'$;
+%		\State Generate the fresh result action $ra$;
+%		\State Combine $C, B, ra$ as a new vector $v$;
+%		\For{each $(e_1 \in v )\&\& (e_2 \in sv')$}
+%			\If{$(e_1\ is\ null\ \&\&\ e_2\ is\ not\ null)\ ||\ (e_1\ is\ not\ null\ \&\&\ e_2\ is\ null)$} 
+%			\State Skip;
+%			\Else ~ Add $(e_1 = e_2)$ into the $Pred$;
+%			\EndIf
+%		\EndFor
+%		\State Generate the result open transition $ot$ with $Pred$;
+%		\State Add the $ot$ into $L_{ot}$;
+%	\EndFor
+%\EndFor 
+%\State \Return $L_{ot}$;
+%
+%\end{algorithmic} 
+%\end{algorithm}
+
+\paragraph{Matching:} 
+\QIN{$Given a synchronization vector ~ SV_k\in SV = (a'_i)^{i\in I} (b'_j)^{j\in J}\rightarrow v' , G_k , k\in K$, and a tuple
+$C_n\in \texttt{COMB} = {(v_i)}^{i\in I} , n\in N$ where $K$ and $N$ are the indices of the set elements.
+As the behavior of subnets should match with the synchronization vector to compose the subnets.
+The matching method tries matching $SV_k$ and $C_n$ to generate the predicates.
+According to the definition of predicate, the hole behaviors $Hole$ and result action $v$ are also involved. 
+}
+
+\QIN{
+$$Matching(SV_k, C_n, Hole, v) = 
+\begin{array}{l}
+\forall {(a'_i)}^{i\in I},
+{(b'_j)}^{j\in J},v'.
+\\
+v_i=a'_i\land \, b_j=b'_j \land v=v' \land G_k
+\end{array}$$
+which is exactly the new part of predicate for one possible result.
+}
+%Algorithm 3 shows the algorithm matches
+%combination $L_C$, hole behaviors $B$ with synchronization vectors
+%$SV$ according to the definition of the predicate declared before. We
+%clone the $sv$ using the fresh function to generate a new $sv'$ with
+%fresh variables.The mismatch on working status is easy to detect so we
+%filter them in the algorithm through checking the matching elements
+%$e_1$ and $e_2$. 
+%Then we build the resulting open transition. Satisfiability of the
+%predicate is not checked at this level, but only later, at the
+%toplevel of the pNet.
+
+\paragraph{Filtering:} 
+\QIN{There is already able to filter some wrong open transitions during the matching.
+We can ensure that the synchronization vector is not matched with the subnets if there is only one side not involved.
+Then we can remove the transitions from the result of matching according to the condition $\gamma$ where
+$\gamma = \bigcup_{i\in I}(v_i\in\eta\land a'_i\in\eta)\lor(v_i\in\eta\land a'_i\in\eta) .$
+}
 
@@
 %% \end{figure}
+
+\subsection{Transition to SMTlib}
+In order to submit satisfiability problems to Z3 (for the predicates
+in open transitions), we need to generate SMTlib programs, from the
+pNet Algebra presentation and predicates.
+More precisely, we need to translate to SMTlib:
+\begin{itemize}
+  \item the presentation of the action algebra
+    (sorts and operators) that is defined for a given language (process calculus, or high level programming language),
+    \item for a given pNet, the set of local constants (actions or auxiliary data) that are used in the pLTSs,
+    \item for each open transition: the declaration of variables, and
+      the predicate (including action expressions).
+\end{itemize}
+
+During this translation, in order to guarantee that the generated code
+will cause no runtime errors during parsing and execution, we need
+to ensure that all objects used in the SMTlib code are properly
+declared, and that they are correctly typed.
+
+Note that in principle, such an algebra correspond to a given
+high-level language (e.g. a process algebra), and that the algebra
+presentation will be defined once and for all in the framework of the
+pNet semantics of each specific language.
+
+\subsubsection{Algebra presentations}
+
+\begin{definition}
+  An Algebra Presentation is a pair $\mathcal{P}=<Sorts,Constrs,Ops>$ where:
+  \begin{itemize}
+  \item $Sorts$ is a set of Sort names
+    \footnote{Later we may want to extend this with Sort constructors,
+      like Array or Pair, but this is not needed now}
+  \item $Constrs$ is a set of constructor operators, with $Con$ the
+    constructor name, and arity: $arity(Con)=n \in \mathbb{N}$,
+    and with their signature and their associated selectors,
+    of the form: '$Con : (sel_1,sort_1), ... , (sel_n,sort_n) -> sort$'.
+    For each argument, the pair $(sel_i,sort_i)$ defines an auxiliary
+    operator of name $sel_i$ with signature $sel_i : sort -> sort_i$.
+    \item $Ops$ is a set of other (auxiliary) operators, with their
+      arity and signature, of the form: $Op : sort_1, ...  sort_n ->
+      sort$
+      \item $Constrs(sortname), Sels(sortname)$, respectively define the set of
+        constructors and selectors of sort $sortname$
+  \end{itemize}
+  All sorts and operator names must be distinct.\\
+  Amongst Constructors, those of arity 0 are called constants, and we
+  define $Consts(\mathcal{P}) = \{Con \in Constrs. arity(Con)=0\}$.
+\end{definition}
+
+We have a minimal, predefined algebra presentation for all pNets, including
+three basic sorts $Bool$, $Action$ and $Int$ and their
+operators. Table \ref{Table:predefinedSorts} defines these elements.
+
+In addition, and for convenience, we provide one generic construct for
+parameterized actions named FUN, which can accept any number of
+arguments of any sort. The result type, though, can only be $Action$,
+in order to keep the type-checking simple (see next section).
+
+\begin{table}\caption{\label{Table:predefinedSorts}\leftline{Algebra Presentation: predefined Sorts
+  and Operators}}
+	\begin{tabular}{p{3cm}p{3cm}p{6cm}}
+		\hline\specialrule{0em}{1pt}{1pt}
+		Sort & Constructors & Other Operators
+                \\\specialrule{0em}{1pt}{1pt}
+		\hline\specialrule{0em}{3pt}{3pt}
+		Bool    			&
+                $\texttt{true},\ \texttt{false}$&
+                $\land,\ \lor$
+                \\\specialrule{0em}{1pt}{1pt} 
+		Action 			&  $\texttt{FUN}$ &
+                \\\specialrule{0em}{1pt}{1pt}
+		Int 				&
+                ${0, \{i, -i\}_{i \in \texttt{Nat}}}$  &
+                $- \texttt{(unary)},\ +,\ -
+                \texttt{(binary)},\ \times,\ \div, \texttt{etc.}$
+                \\\specialrule{0em}{1pt}{1pt}
+                \textsl{for any sort} & & $=,\ \ne$
+		\\\hline
+	\end{tabular}
+\end{table}
+
+For a given language, or for a given use-case, the designer can
+declare more sorts and operators, using our pNet API.
+As an example, a (value-passing) CCS action algebra, where we assume a
+single auxiliary value domain ``Data'', can be defined as:
+
+\begin{example}
+  \begin{itemize}
+  \item $Sorts_{CCS} = \{Action, Channel, Data, Int, Bool\}$
+  \item $Constrs_{CCS} =\\
+    \texttt{Emit}: 2, \{(Chan\_E:Channel),(Value\_E:Data)\}->Action\\
+    \texttt{Receive}: 2, \{(Chan\_R:Channel),(Value\_R:Data)\}->Action\\
+    \texttt{Tau}: 0, \{\}-> Action\\
+    \texttt{... and all predefined operators}$
+  \end{itemize}
+\end{example}
+
+\begin{lstlisting}
+AlgebraSort Action = new AlgebraSortImpl("Action");
+AlgebraSort Channel = new AlgebraSortImpl("Channel");
+AlgebraSort Data = new AlgebraSortImpl("Data");
+Action.addConstructor("Emit", 
+	{"Chan_E", "Value_E"}, {Channel, Data});
+Action.addConstructor("Receive", 
+	{"Chan_E", "Value_E"}, {Channel, Data});
+Action.addConstructor("Tau");
+\end{lstlisting}
+
+\TODO{[DONE][Xudong]: Give an example of defining $Tau$ and $Emit$ using the (new
+  version of) the API}
+
+\subsubsection{Expressions}
+Once an algebra presentation is defined, we can construct expressions
+of the term algebra, using variables and operators:
+
+\begin{definition}
+  Let $\mathcal{V}$ be a set of variables. The Term Algebra
+  $\Sigma_{\mathcal{P},\mathcal{V}}$ is the set of:
+  \begin{itemize}
+  \item variables $x \in \mathcal{V}$
+  \item terms (or expressions) $op (arg_1, ... , arg_n)$ with $op$ an operator in
+  $\mathcal{P}$ of arity $n$, and each $arg_i$ an expression.
+  \end{itemize} 
+\end{definition}
+
+\paragraph{Constants and variables in pNets and in open transitions}
+
+In addition to the objects defined in the Algebra Presentation, there are
+specific objects that are introduced by the pNet construction, and by
+the semantic rules used to build the open transitions and their
+predicates. This includes, for a pNet $pnet$
+\begin{itemize}
+\item $Const(pnet)$: Constants from the pLTSs (controllers) transitions: these are
+  new constant constructors, usualy of sort Action, local to an
+  instance of a controller. The pNet definition requires that all
+  these constants are distinct from each other.
+\item $SVars(pnet)$: State variables of the controllers. Here also they are required
+  to be distinct from those of other controllers.
+\item $IVars(pnet)$: Input variables of the controllers.
+\item $FVars(pnet,ot)$: Several kinds of ``fresh'' variables, created by application of
+  rule Tr2, during the construction of each open transition $ot$:
+  Action variables for the behavior of holes and the 
+  resulting actions of transitions, variables created during the cloning
+  of synchronisation vectors.
+\end{itemize}
+
+\def\EPres{\mathcal{P}}
+\def\EEnv{\Gamma}
+
+All variable sets above include their sort.
+To define the typing rules for expressions and the translation
+functions, for any pNet $pnet$ and open transition $ot$, we define an
+extended presentation $\EPres_{pnet}$ and environment $\EEnv_{pnet,ot}$ that includes all of the
+objects above:
+
+\begin{definition}
+  Given an algebra presentation $\mathcal{P}_{pnet}=<Sorts,Constrs,Ops>$ and a pNet $pnet$, we
+  construct:
+  \begin{itemize}
+  \item An extended presentation $\EPres_{pnet}<Sorts,Constrs \cup Const(pnet),Ops>$.
+  \item For a given open transition $ot$, an environment
+    $\EEnv_{pnet,ot}=SVars(pnet) \cup IVars(pnet) \cup FVars(pnet,ot)$. 
+  \end{itemize} 
+\end{definition}
+
+\paragraph{Well-formed and well-typed expressions}
+
+The purpose of this section is to define static semantic notions that
+will guarantee that the translation to the SMT language will be
+correct, i.e. will not yield errors at runtime. This includes
+well-formness (all sorts, operators, variables are defined, and
+expressions respect the arity of operators), and typing rules.
+
+\begin{definition}
+  Given a presentation $\EPres$ (possibly extended) and an environment $\EEnv$:
+  \begin{itemize}
+  \item $\EEnv$ is well-formed if all sorts in $\EEnv$ are
+    defined in $\EPres$
+  \item an expression is well-formed if all its operators are defined
+    in $\EPres$, and used with the proper arity, and all its
+    variables are defined in $\EEnv$
+  \item an expression is well-typed if it can be typed by the typing
+    rules in table \ref{table:typing-rules}
+  \end{itemize}
+\end{definition}
+
+The following judgment, and the typing rules in table
+\ref{table:typing-rules} can be used to check both the wellformedness
+and well-typing of expressions in a pNet or in an open transition,
+given the corresponding $\EPres$ and $\EEnv$.
+
+%\begin{table}\caption{\leftline{Typing judgment for Expressions in Open pNets}}
+\vspace{1ex}
+\noindent
+\begin{tabular}{p{5cm}p{7cm}}
+		\hline\specialrule{0em}{3pt}{3pt}
+%%		$\EEnv \vdash \diamond$ 					& $\EEnv$ is a well-formed environment 					\\\specialrule{0em}{1pt}{1pt}
+%%		$\EEnv \vdash A$ 							& A is a well-formed type in $\EEnv$	 					\\\specialrule{0em}{1pt}{1pt}
+		$\EPres,\EEnv \vdash M: A$
+                & M is a well-formed term of type A in $\EPres,\EEnv$			\\\specialrule{0em}{1pt}{1pt}
+		\specialrule{0em}{3pt}{3pt}\hline
+	\end{tabular}
+%\end{table}
+
+\begin{table}\caption{\leftline{Type Rules for Open pNets}}
+  \label{table:typing-rules}
+	\begin{tabular}{p{5cm}p{5cm}p{2.5cm}}
+		\hline\specialrule{0em}{3pt}{3pt}
+		%% (Env $\varnothing$) 								
+		%% & 										
+		%% &					\\\specialrule{0em}{1pt}{1pt}
+            %% $\dfrac{ }{\varnothing \vdash \diamond}$			
+            %% & %$\dfrac{\EEnv \vdash A ~~ x\ }{\varnothing \vdash \diamond}$
+            %% &					\\\specialrule{0em}{3pt}{3pt}
+		%% (Type Bool) 										
+		%% &(Type Action) 						
+		%% &(Type Int)			\\\specialrule{0em}{1pt}{1pt}
+		%% $\dfrac{\EPres \vdash Bool~~\EEnv \vdash \diamond}{\EPres,\EEnv \vdash Bool}$ 
+		%% & $\dfrac{\EPres \vdash Action~~\EEnv \vdash \diamond}{\EPres,\EEnv \vdash Action}$ 
+		%% & $\dfrac{\EPres \vdash Int~~\EEnv \vdash \diamond}{\EPres,\EEnv \vdash Int}$        \\\specialrule{0em}{3pt}{3pt}
+		(Var x) 										
+		& 						
+		&			\\\specialrule{0em}{1pt}{1pt}
+		$\dfrac{\EEnv \vdash x:A}{\EPres,\EEnv \vdash x:A}$ 
+		&  
+		&       		\\\specialrule{0em}{5pt}{5pt}
+		\multispan{2} (Binary operators, e.g.: $\land, \lor$ for booleans, $+, -, \times, \div, \le, \ge$ for integers, etc.)
+
+		& 			\\\specialrule{0em}{3pt}{3pt}
+		$\dfrac{\EPres \vdash BinOp :: ty1, ty1 \rightarrow ty2 ~~\EEnv \vdash x_1:ty1 ~~\EEnv \vdash x_2:ty1}{\EPres,\EEnv \vdash x_1 ~BinOp~ x_2:ty2}$ 
+		& 
+		&       		\\\specialrule{0em}{3pt}{3pt}
+		\multicolumn{2}{l}{(Unary operators, e.g. $\lnot$ for booleans, - for integers)}
+
+		& 			\\\specialrule{0em}{3pt}{3pt}
+		$\dfrac{\EPres \vdash UnOp :: ty1 \rightarrow ty2 ~~\EEnv \vdash x:ty1}{\EPres,\EEnv \vdash Unop~x:ty2}$   
+		&&       		\\\specialrule{0em}{5pt}{5pt}
+		(Polymorphic EQ and NEQ)							
+		&					
+		&
+                                         \\\specialrule{0em}{3pt}{3pt}
+		$\dfrac{\EPres \vdash A  ~~\EEnv \vdash x_1:A ~~\EEnv \vdash x_2:A}{\EPres,\EEnv \vdash x_1 = x_2:Bool}$ 
+		& 
+		$\dfrac{\EPres \vdash A  ~~\EEnv \vdash x_1:A ~~\EEnv \vdash x_2:A}{\EPres,\EEnv \vdash x_1 \ne x_2:Bool}$
+
+		&       		\\\specialrule{0em}{5pt}{5pt}
+		(Overloaded FUN)							
+		&					
+		& 			\\\specialrule{0em}{3pt}{3pt}
+		$\dfrac{\EPres \vdash \texttt{FUN} :: A_1,...,A_n \rightarrow Action ~~\EPres \vdash A_1~~...~~\EPres \vdash A_n ~~\EEnv \vdash x_1:A_1~~...~~\EEnv \vdash x_n:A_n}{\EPres,\EEnv \vdash \texttt{FUN}(x_1,...,x_n):Action}$
+		& 
+		&			\\
+		\specialrule{0em}{5pt}{5pt}\hline
+	\end{tabular}
+\end{table}
+
+\begin{remark}
+  These rules provide a simple type-checking algorithm: if all
+  variables in an expression are known in $\EEnv$, then a bottom-up
+  application of the rules will decide whether the expression is
+  well-typed, and compute the type of each sub-expression.
+\end{remark}
+
+\subsubsection{Map to SMT-LIB language}
+The pNet elements, as defined above, can be full translated into
+SMT-LIB language, but there are a number of differences in the
+structure of the models/langages, so the translation is not trivial.
+
+In this section we shall define separately the translation of the
+(extended) algebra presentation for one pNet (so it will be fixed for
+the study of one use-case); and the translation of each predicate in
+the context of an open-transition of this pNet.
+
+\def\translate{~\lhook\joinrel\longrightarrow}
+
+\vspace{1ex}\noindent
+%\begin{table}\caption{\leftline{Mapping}}
+	\begin{tabular}{p{3cm}p{9cm}}
+		\hline\specialrule{0em}{1pt}{1pt}			
+		(Presentation)							
+		&								\\\specialrule{0em}{1pt}{1pt}		
+		&$Sorts \& Constructors \translate$	declare-datatypes				\\\specialrule{0em}{1pt}{1pt}
+		&$Operators \lhook\joinrel\longrightarrow$	declare-function		\\\specialrule{0em}{1pt}{1pt}
+		(Predicate)							
+		&								\\\specialrule{0em}{1pt}{1pt}
+		&$\EEnv ~~\lhook\joinrel\longrightarrow$	declare-const		\\\specialrule{0em}{1pt}{1pt}
+		&$Pred ~~\lhook\joinrel\longrightarrow$	 assert		\\\specialrule{0em}{1pt}{1pt}
+		&$\texttt{FUN}(x_1,...,x_n)$		\\\specialrule{0em}{1pt}{1pt}
+		&$\texttt{pNet expression} ~~\lhook\joinrel\longrightarrow$ SMTLib expression	\\\specialrule{0em}{1pt}{1pt}
+		&$...$	\\\specialrule{0em}{1pt}{1pt}
+		\specialrule{0em}{1pt}{1pt}\hline
+	\end{tabular}
+%\end{table}
+
+\smallskip
+\ERIC{My plan here is to provide the translation principles as some
+  high-level pseudo code, together with precise definition of the
+  translation functions of a presentation+environment, and of a
+  predicate (including expressions)}
+
+In the following definitions, we use abstract functions corresponding to
+SMTlib/Z3 constructs. In practice they can be implemented either as
+SMTLib scripting programs, or as calls to the Z3 java API.
+
+\subsubsection{Presentation Translation}
+We define here the translation of the algebra presentation, extended
+with the constant operators collected from the pNet. It produces the
+declaration of sorts (excepted Bool and Int) with their constructors
+and selectors as \texttt{declare-datatypes}, and the declaration of
+other operators as \texttt{declare-function} constructs.
+For sorts, we must distinguish the case of mutually defined sorts
+(e.g. edges and vertices in a graph), that must be declared within a
+single \texttt{declare-datatypes} construct. For this we define:
+
+\begin{definition}
+Define the (strict) order "is-using" between sorts $S1 is-using S2$ iff $S2$
+occurs as the sort of one argument in the constructors of $S1$.
+\end{definition}
+
+\TODO{[Xudong: this is certainly obsolete?] At the same time, we have
+  several internal lists (actually hash 
+  maps) \texttt{exprs}, \texttt{funcDecls}, \texttt{sortDatatypes} to
+  store the generated Z3 objects with their names for later proofs.}
+
+\begin{lstlisting}
+Let Pres = <Sorts, Constrs, Ops> an extended presentation
+(i.e. including the constants from the pnet),
+- define MySorts = Sorts \ {Bool, Int}
+- compute the strongly connected components in the graph
+  of MySorts with respect to the relation is-using
+- for each SCC in this graph, construct: 
+  dataype-declaration = TrPresentation (Pres, SCC)
+- for each other operator op in Ops, construct:
+  function-declaration = TrPresentation (Pres, op)
+\end{lstlisting}
+
+%\begin{table}\caption{\leftline{Rules for TrPresentation}}
+%  \label{table:TrPresentation}
+\noindent
+\begin{tabular}{p{5cm}p{5cm}p{2.5cm}}
+		\hline\specialrule{0em}{3pt}{3pt}
+		\multicolumn{2}{l}{One datatype declaration for each SCC}
+
+		& 			\\\specialrule{0em}{1pt}{1pt}
+		$\dfrac{name=name(Sort) \qquad constrs=Constrs(name) %\qquad sels=Sels(name)
+                  \translate constrs}
+                       {SCC \translate
+                  \texttt{(declare-datatypes () $name$ (map $\translate constrs$))}}$
+
+		&&       		\\\specialrule{0em}{1pt}{1pt}
+		\multicolumn{2}{l}{Constants: }
+
+		& 			\\\specialrule{0em}{1pt}{1pt}
+		$\dfrac{arity(constr)=0}
+                       {constr \translate \texttt{name($constr$)}}$
+
+		&&       		\\\specialrule{0em}{1pt}{1pt}
+		\multicolumn{2}{l}{Other constructors: }
+
+		& 			\\\specialrule{0em}{1pt}{1pt}
+		$\dfrac{n = arity(constr) \neq 0 \qquad |sels|=n
+                  \qquad sels =  BuildSels(constr)}
+                       {constr \translate \texttt{(name($constr$) . sels)}}$
+
+		&&       		\\\specialrule{0em}{1pt}{1pt}
+		\multicolumn{2}{l}{Other operators: }
+
+		& 			\\\specialrule{0em}{1pt}{1pt}
+		$\dfrac{op : sort_1, ..., sort_n : sort}
+                       {op \translate \texttt{(declare-fun name($op$) ($sortname_1
+                           ... sortname_n$) $sortname$)}}$
+
+		&&       		\\\specialrule{0em}{1pt}{1pt}
+		\multicolumn{2}{l}{Special case of FUN: }
+
+		& 			\\\specialrule{0em}{1pt}{1pt}
+		$\dfrac{}
+                       {FUN \translate \texttt{map $\translate CollectFunTypes(pNet)$ }}$
+
+		&&       		\\\specialrule{0em}{1pt}{1pt}
+		$\dfrac{}
+                       {argstypes \translate \texttt{(declare-fun
+                           $BuildFunInstance(argstypes)$ (map name
+                           $argstypes$) Action) }}$
+
+		&&       		\\\specialrule{0em}{1pt}{1pt}
+		\hline
+\end{tabular}
+%\end{table}
+
+\smallskip
+Where:
+\begin{itemize}
+  \item the $BuildSels$ function, for a constructor with $n$ arguments,
+argument sorts $sort_i$, and selector names $sel_i$, builds the list
+$\{(sel_i, sort_i)\}_{i\in[1..n]}$.
+\item the $CollectFunTypes$ function collects all possible instances
+  of the overloaded FUN argument types found in the pNet, as computed by the typing
+  rules; and $BuildFunInstance$ use these argument types as suffixes
+  to disembiguate 
+\end{itemize}
+
+\begin{example}
+  For the CCS presentation above, we would get (in SMTLib syntax):
+\begin{lstlisting}
+  (declare-datatypes Data ())
+  (declare-datatypes Channel ())
+  (declare-datatypes ()
+      ((Action (Emit (Chan\_E Channel) (Value\_E Data))
+               (Receive (Chan\_R Channel) (Value\_R Data))
+               Tau )))
+  \end{lstlisting}
+\end{example}
+
+\TODO{Need to add an exemple with 2 instances of FUN}
+
+\subsubsection{Predicate translation}
+
+\QIN{Each time we submit each open transition to Z3 module, we translate
+  its predicate into Z3 language format and send it for satisfiability
+  checking. Every term of the predicate is declared as an
+  \texttt{assert} in Z3. A constant action or a parameterized
+  expression is easy to get from the internal list storing the objects
+  while all the variables are not declared at the beginning. So we
+  declare them before the submission of a predicate term with the API
+  method conducting \texttt{declare-const}.}
+
+The second part of the translation function is called for each open
+transition. More precisely we need here:
+
+\begin{lstlisting}
+Let Pres = <Sorts, Constrs, Ops> be the extended presentation
+and OT = <Leaves, Holes, Pred, Assign> an open transition.
+- compute the environment $\EEnv=\EEnv_{pnet,OT}$ collecting
+all variables used in OT
+- check that all pLTS labels (action, guard, assignement) in
+the transition, the OT predicate, and the OT assignments are
+well-formed and well-typed
+- for each variable $v$ in $\EEnv$, construct:
+  define-const = TrPredicate ($\EEnv,v$)
+- turn the predicate into conjunctive normal form
+- for each conjunct $P_i$ in the predicate, construct:
+  assert = TrPredicate $(P_i)$
+\end{lstlisting}
+
+\noindent
+\begin{tabular}{p{5cm}p{5cm}p{2.5cm}}
+		\hline\specialrule{0em}{3pt}{3pt}
+		\multicolumn{2}{l}{Variables}
+
+		& 			\\\specialrule{0em}{1pt}{1pt}
+		$\dfrac{\EEnv \vdash x:A }
+                       {x \translate \texttt{(declare-const x A)}}$
+
+		&&       		\\\specialrule{0em}{1pt}{1pt}
+		\multicolumn{2}{l}{Predicate conjunct: }
+
+		& 			\\\specialrule{0em}{1pt}{1pt}
+		$\dfrac{}
+                       {P_i \translate \texttt{(assert ... }}$
+
+		&&       		\\\specialrule{0em}{1pt}{1pt}
+		\multicolumn{3}{p{12cm}}{To be completed with translation of
+                expressions, including special cases for EQ, NOT\_EQ,
+                and FUN }
+
+		 			\\\specialrule{0em}{1pt}{1pt}
+		\hline
+\end{tabular}
 
@@
 \centerline{$\OTvar{assert (or (= var\_s0 0) (= var\_s0 01)))}$}
+
+\subsection{Simplification of Predicates}
+\QIN{
+We apply several structural rules to generate the predicates restricting the composition of the subnets by synchronization vectors.
+The predicates may contain some redundancy if there are variables in middle level are matching other variables both in lower and higher level at the same time. 
+}
+
+We already have the operational semantics of open pNets restricting the open transitions using two rules.
+The generated equations in the $predicates$ contain either intermediate variables or ground ones, but what we want is the equation between ground terms.
+
+\QIN{
+We want to reason about the equations to eliminate the redundancy. 
+Considering pNet has a special tree-structure, the replacement between equations should be one-way, the direction is from leaves to the top level, until the root pNet node. 
+And it is easy to figure out the intermediate variables by the constraint rules.
+While it is not needed figure out if an equation is "true" , it can be left to Z3.
+}
+
+\begin{definition}[Intermediate Variable]
+\paragraph{}
+When applying Tr1, we do not collect intermediate variables.
+Though the result action might be the intermediate one between two result action from the SV if it is not the root of the pNet, it will be determined at the higher level instead of at the leaves.
+
+\begin{description}
+	\item[{\bf Using the parameters from Tr1:}]
+\end{description}
+
+\[ InterVar(OT) = \emptyset \]
+
+\paragraph{}
+When it comes to a pNet node, all the variables from the sources mentioned above should be contained in the $InterVar$ together with the intermediate variables from the subnets.
+Whatever its subnet is a pLTS or pNets.
+At the same time, the subnet's result action should be add into the $InterVar$.
+
+If the result of the SV also occurs in its parameters, it means the action from the subnet will be propagated as the result action of the open transition on this level through this SV result action.
+So it is also the intermediate variable in such situation.
+
+\begin{description}
+	\item[{\bf Using the parameters from Tr2:}]
+\end{description}
+\[ InterVar(OT) = \bigcup_{m\in I_k}{InterVar(OT_m)}  \bigcup_{m\in I_k}{\{v_m\}} \cup{InterVar(SV_k)} \]
+$$ InterVar(SV_k)=\left\{
+\begin{aligned}
+\emptyset & , & \alpha_{k}^{'} \not\in \bigcup_{m\in I_k \uplus J_k}{\{\alpha_{m}\}}\\
+{\alpha_{k}^{'}} & , & \alpha_{k}^{'} \in \bigcup_{m\in I_k \uplus J_k}{\{\alpha_{m}\}}
+\end{aligned}
+\right.
+$$
+
+\begin{itemize}
+	\item $OT$ is an open transition.
+	\item $I, J$ is the set of indices.
+	\item $k$ is the indices of the synchronization vectors.
+	\item $SV$ is the set of the synchronization vectors.
+	\item $Vars()$ is the function that gets all the variables in the object.
+	\item $\alpha$ and $\alpha^{'}$ is the element of the  the synchronization vector.
+\end{itemize}
+\end{definition}
+
+Definition of the intermediate variable shows that elimination should be done every time Tr2 is applied.
+
+%\texttt{\\
+%1. Classify the ground and intermediate variables.
+%\begin{itemize}
+%    \item (1) The predicates of the subnets: The result actions of the sub-OTs. Others are ground.
+%    \item (2) The chosen synchronization vector: If the result is also one of the elements, it is also the intermediate variable. Otherwise, all of the parameters are ground.
+%    \item (3) Hole behaviors: Ground.
+%    \item (4) The result action: Not sure. But it must be ground if it is on the root node.
+%\end{itemize}
+%2.
+Using a list {\em equations} to store the equations containing the intermediate variable.
+{\em equations} is a hasp map storing the corresponding ground terms of the variable by its name.
+Its structure likes <String, List<Expression> >.
+It will be updated during the later deduction .\\
+%3. The guards from the subnets are kept, waiting for further substitution.\\
+%4. Deduct out the new equations using the redundant Pred got in matching().\\
+%    Checking two sides of the equations.
+%\begin{itemize}
+%   \item If both are ground, then generate a new equation with them, add it to Pred.
+%   \item If the right-hand-side or left-hand-side is intermediate, then find the ground term of it from the list then generate a new equation and add it to Pred.
+%   \item If both are intermediate, then check the list {\em equations}
+%   	\begin{itemize}
+%  		\item If list contain both lhs and rhs, then get the corresponding ground terms of them, generate the new equation with the ground terms. Add it to Pred.
+%   		\item If list only contain lhs, store the rhs in {\em equations} with lhs's corresponding ground terms.
+%   		\item If list only contain rhs, store the lhs in {\em equations} with rhs's corresponding ground terms.
+%   		\item Otherwise, skip this turn.
+%         \end{itemize}
+%\end{itemize}
+%5. Search the inter in the guards if it is found, subsititute it with the ground. Then conduct step 2 again.\\
+%}
+
+\paragraph{Term Rewriting Rules}
+Predicates already have a format declaring what it verifies. According to that previous work, we define the predicates.
+Let $\mylangle\overline{\pNet},\overline{S},\symb{SV}_k^{k\in K} \myrangle$
+be a pNet. Choose a synchronisation vector $SV=clone(SV_k) ={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v' \, ,G_k $, for $k\in K$. The
+predicate $\Pred$ relating
+the actions of the involved sub-pNets and the resulting actions.
+\begin{definition}[Predicate]
+\[\Pred(SV, \overline{\pNet},\overline{S}, v) = 
+\begin{array}{l}
+\forall {(a'_i)}^{i\in I},
+{(b'_j)}^{j\in J},v'.
+\\
+v_m=a'_i\land \, b_j=b'_j \land v=v' \land G_k
+\end{array}\]
+\end{definition}
+\QIN{
+The new predicates introduce more hypotheses for term rewriting. However, not every variable can be substituted. 
+Here we introduce several rewriting rules.
+}
+
+\begin{align*}
+   &v_m=a'_i \land v_m=v'_m \rightarrow a'_i = v'_m &[RL-1]\\\\
+   &v_m=a'_i \land v=v' \rightarrow v_m=v ~~ \texttt{if} ~~ a'_i = v', ~~ a'_i,v' \in InterVar &[RL-2]\\\\
+   &v_m=foo'_i(a_1,...,a_p,...,a_n) \land v=v' \rightarrow v_m=foo'_i(a_1,...,v,...,a_n) \\ 
+   &\hspace{15em}\texttt{if} ~~ a_p = v', ~~ a_p,v \in InterVar &[RL-3]\\\\
+   &b_j=b'_j \land v=v' \rightarrow b_j=v ~~ \texttt{if} ~~ b'_j = v', ~~ b'_j,v' \in InterVar &[RL-4]\\\\
+   &b_j=foo'_i(a_1,...,a_p,...,a_n) \land v=v' \rightarrow b_j=foo'_i(a_1,...,v,...,a_n) \\ 
+   &\hspace{15em}\texttt{if} ~~ a_p = v', ~~ a_p,v \in InterVar &[RL-5]\\\\
+\end{align*}
+
+\QIN{
+Rule RL-1 applies on when the result action of subnets matching other arguments of the chosen SV. It merges the predicates from the subnets with the new generated predicates.
+Rule RL-2 shows that if the result of the SV is also in its arguments, we can straightly get an equation between the subnet action and  the result action.
+RL-3 is the situation that there is an expression instead of a variable contains an intermediate argument.
+The substitution will only occur on the argument.
+Actually, what happened is similar if there is a hole behavior instead of a subnet result action attending in the equation.
+So we get RL-4 and RL-5.
+However, every hole behavior should be kept through out the computing.
+That's why there no rule similar to the RL-1 for hole behaviors.
+}
 
@@
 \subsection{Term algebra: type system and static semantics}
+\subsection{Fresh variables}
+
+%The variables in each synchronization vector are considered local, so
+%does the variables of an open transition such as its hole behaviors
+%and its result action. So we want rename the variables to make them
+%unique on every occurrence of a vector. Similarly, the name given to
+%the hole behaviors for each hole or the result action for each open
+%transition must be distinct. At the same time, we also hope them still
+%readable. Here we rename the variables with a regular format using the fresh function.
+
+Application of the semantic rules require generating a lot of fresh
+names, for different kind of variables. We could use a global name
+generator to guarantee unicity, but 
+at the same time, we also hope them still
+readable. Here we rename the variables with a regular format using the fresh function.
+More precisely, the fresh function generates a new name adding a
+suffix after the original name. The suffix contains three parts
+combined by a colon.
+
+\begin{definition}[Fresh variable]\label{fresh-variable}
+The format of \emph{fresh variable} (renaming) is defined as:
+``$\emph{prefix : tree\ index\ :\ counter}$''.
+\begin{itemize}
+   \item[$\bullet$] $prefix$ identifies the kind of the
+     variable. current kinds are: sva (SV action), ra (result action), hb (hole behavior).
+   \item[$\bullet$] $tree\ index$ is the index of the node containing the variable in the tree-like structure of the pNet.
+   \item[$\bullet$] $counter$ is the current value of the corresponding counter.
+\end{itemize}
+\end{definition}
+
+%\TODO{Option: Add the process and the vector ids ?}
+
+%$Prefix$ avoids the confusion between variables from different structures with the same name by attaching the type of the structure.
+$Tree\ index$ is given to every node of the pNets to mention which node the variable belongs to as pNets has a tree-like structure.
+To each node, the tree index is always a number sequence of the tree index of its higher level and the index of the node in this level at the last.
+$A\ set\ of\ counters$ is used to count the current times the SV, Hole, subnet invoked, or the number of possible OT generated to provide an identity.
+
+For example, in the running example, the first possible behavior of
+the hole, it doesn't have a name, only have the prefix ``hb''. The
+hole is the second subnets of the root node so its ``tree index'' is
+``12''. The fresh variable name is ``$\OTvar{:hb:12:1}$''. 
 \subsection{Variable managment}

### 2018-01-12 2017-Xudong-SMT/FM-2018-extended.tex
Update the appendix.
Some are moved from the corresponding sectoins.

@@
 \usepackage[T1]{fontenc}
-%\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
-%\geometry{a4paper}                   % ... or a4paper or a5paper or ...
+\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
+\geometry{a4paper}                   % ... or a4paper or a5paper or ...
 %\geometry{landscape}                % Activate for for rotated page geometry
@@
 communications.
+\QIN{
+\paragraph*{Algebra presentations}
+\begin{definition}
+  An Algebra Presentation is a pair $\mathcal{P}=<Sorts,Constrs,Ops>$ where:
+  \begin{itemize}
+  \item $Sorts$ is a set of Sort names
+    \footnote{Later we may want to extend this with Sort constructors,
+      like Array or Pair, but this is not needed now}
+  \item $Constrs$ is a set of constructor operators, with $Con$ the
+    constructor name, and arity: $arity(Con)=n \in \mathbb{N}$,
+    and with their signature and their associated selectors,
+    of the form: '$Con : (sel_1,sort_1), ... , (sel_n,sort_n) -> sort$'.
+    For each argument, the pair $(sel_i,sort_i)$ defines an auxiliary
+    operator of name $sel_i$ with signature $sel_i : sort -> sort_i$.
+    \item $Ops$ is a set of other (auxiliary) operators, with their
+      arity and signature, of the form: $Op : sort_1, ...  sort_n ->
+      sort$
+      \item $Constrs(sortname), Sels(sortname)$, respectively define the set of
+        constructors and selectors of sort $sortname$
+  \end{itemize}
+  All sorts and operator names must be distinct.\\
+  Amongst Constructors, those of arity 0 are called constants, and we
+  define $Consts(\mathcal{P}) = \{Con \in Constrs. arity(Con)=0\}$.
+\end{definition}
+}
 
@@
 \paragraph{Filtering:}
-\QIN{There is already able to filter some wrong open transitions during the matching.
-We can ensure that the synchronization vector is not matched with the subnets if there is only one side not involved.
-Then we can remove the transitions from the result of matching according to the condition $\gamma$ where
-$\gamma = \bigcup_{i\in I}(v_i\in\eta\land a'_i\in\eta)\lor(v_i\in\eta\land a'_i\in\eta) .$
-}
 
@@
 
-\subsection{Transition to SMTlib}
+\subsection{Translation to SMTlib}
+
+\paragraph{Presentation of algebra}
+
+\TODO{Improve this, inserting the main definition from the ``Checker'' document}
+%% Open pNet framework provides us
+%% with a model able to express the semantics of many different algebras
+%% or languages. In particular,
+As seen in section
+\ref{section:pnets}, the \emph{term algebra} used to express the
+action expressions and data parameters is left open in
+the pNet definition.
+
+So, for a given language, we now need to specify its data and action
+domains, giving them an abstract syntax (sorts, constructors, operators,
+and predicates). We call this a \emph{Presentation}.
+We also define a concrete syntax, that will be used for
+pretty-printing, but also for translating the presentation, and the
+predicates, into Z3 syntax (see the ``declare-datatypes'' statement in
+Fig~\ref{schema:smt-lib}).
+
+An algebra presentation contains:
+
+\begin{itemize}
+	\item Sorts: Constants sets of the algebra or types of the data
+          and actions (integer and boolean sort are implicitly
+          declared).  There \emph{must} be one sort for actions, and
+          eventually others for the types of data
+          parameters. In the LOTOS example, 
+          we have the $Action$ sort: $\OTvar{Action = } \{ l, \delta,
+          r, p, q, acc \} .$
+
+	\item Operators:
+          %Operators used to construct action expressions; they are
+          constructors and predicates for data and action sorts. For
+          instance, in our LOTOS example, we
+          have a generic action constructor ``$ACT$'', taking as
+          argument an action litteral and a data parameter, declared as:
+          $\OTvar{ACT:}\OTvar{< Action, Data >} \rightarrow \OTvar{Action.}$, 
+        \item Constants: The satisfiability solver need to know which
+          actions in the pLTS behaviors are constants (like the $l$, $\delta$, 
+          $r$ of the controllers in running example). 
+          For a given pNet system, the sort $Action$ will include all
+          these constants.
+\end{itemize}
+
+\paragraph{Interaction with Z3}
+%\TODO{1. example input of Z3 in SMT-LIB.[DONE] 2. software architecture.[DONE]}
+%There are several ways to interact with the Z3 solver. 
+%It is possible to use Z3 interactively using the SMT-LIB
+%(Python-based) language. 
+From inside our algorithm code, we submit satisfiability requests to
+Z3 using its JAVA API. Here for readability, we
+show the Z3 code using its SMT-LIB input language. As an
+example in
+Fig~\ref{schema:smt-lib}, we show the input for checking the
+transition of Fig.~\ref{schema:unsat-ot}. It contains the declaration
+of the LOTOS action algebra types 
+and constructors, then the declaration of variables, and finally the
+predicate to be checked, encoded as a set of assertions.
+%% Generally, some $datatypes$ are declared to input the sorts, while here
+%% we only declare one $datatypes$ named $Action$ to involve all the
+%% constant actions. Then we input the predicate of this open transition
+%% in two parts: the variables contained in the predicate are declared
+%% first, then the terms of predicate are inputed as $assertions$ one by
+%% one. 
+The result "unsat" in the output is just what we expected.
+
+%\TODO{edit the figure to make it smaller in height [DONE]}
+
+%We present the architecture of the interaction with Z3 in
+%Fig~\ref{schema:interaction}.
+%For each OT generated at the toplevel of a pNet, the predicate must be
+%submitted for satisfiability check to Z3. For that we need to
+%translate into Z3 (Java-API) syntax, both the elements of the action
+%algebra, and the predicates itself, including the encoding of the
+%variable assignments (the Post part).
+%
+%The $presentation$ of the action algebra
+%is declared at the beginning of the algorithm as the $sorts$ and the
+%$operators$ will be used throughout the whole algorithm. It is
+%translated into $datatypes$ and $functions$ then submitted to the Z3
+%at the same time. Each candidate predicate will then be translated
+%into $assertions$ before submitted to Z3 after the algorithm
+%computing out all the possible open transitions, they act as
+%intermediate results there. Together with the $datatypes$ and
+%$functions$, the $assertions$ are used to check the satisfiability of
+%the predicate in Z3.
+
+To build the input submitted to Z3 for each OT,
+we translate the algebra $presentation$, the predicates and the
+variable assignments (the Post part) into Z3 (Java-API) syntax.
+% The $presentation$ and the predicates are translated separately.
+
+\paragraph{Translation of Action algebra presentation}
+\TODO{Exerpt of the formalisation}
+The $datatypes$ are declared according to the $sorts$ the users
+declared in the $presentation$. If the return type of the $functions$
+is one of the $datatypes$, we add this $function$ to the $datatypes$ declaration.
+So when we declare the operator ACT we illustrated in section 4.1, it
+will be just declared together with the constants like :\\
+\centerline{$\OTvar{(ACT\ (action3\ Action)(data\ Int))}$}
+
+The $functions$ can also be declared independently, it usually applies to functions returning integer or boolean, in the format like:\\
+\centerline{$\OTvar{(declare\text{-}fun\ MAX\ (Int\ Int)\ Int)}$}
+
+%Although in Fig~\ref{schema:smt-lib} we have not declared $functions$ outside of $datatypes$, there still exists $functions$ declared independently.
+The input and output types of the $function$ are also determined by the construct of the  $operators$ in the presentation.
+For example, we define a new operator to present the equation between two actions in LOTOS example $\text{EQUAL}$ in the format likes:
+%
+%\[EQUAL: \quad < Action , Action > \rightarrow Bool .\]
+%
+%It will be translated into the Z3 statement: 
+%
+%\[\text{(declare-fun\ EQUAL\ (Action\ Action)\ Bool) .}\]
+
+\paragraph{Translating assignments into predicate terms}
+\TODO{Exerpt of the formalisation}
+
+%The assignments are also taken into account when checking the
+%satisfiability of the open transitions as they represent the value of
+%the variables involved in an OT. In order to do that, we employs a
+%translation from assignments into term of predicates. The assignments
+%required to be translated are only those belong to the variables
+%contain in the start states of the open transitions. The assignments
+%are represented as equations between the variables and the expressions
+%on the right side of assignment. For the assignments of the same
+%variable, we do not figure out which state is the precursor of current
+%state, we keep all these possible equations instead, and generate the
+%disjunction of these equations. The state could always move to the
+%target state if there exists one of the values of its variable
+%satisfies the guard.
+%%\TODO{It won't matter the variable of the next state
+%%except that the right hand side expression contain its variables. This
+%%is a problem left to be solved in our future work. WHICH PROBLEM ?}
+%After that, for the assignments of the different variables, we generate a conjunction of them. This way we obtain a new term of the predicate involving assignments of the variables.
+
+State-variable assignments are also treated as a part of the
+predicates when checking the satisfiability. % Here we need conduct some
+% translations,
+For each assignement in a $\Post$ predicate, such as $\{s_0 \leftarrow 1\}$ in section
+~\ref{section:op-semantics}, we translate it into an equation
+$s_0=1$. For several assignments of the same variable in the same state,
+we generate the disjunction of 
+these equations. Correspondingly, we generate a conjunction for the
+assignments from different variables.
+
+\paragraph{Checking satisfiability}
+
+% We check the satisfiability of open transitions on the top level of
+% the pNet, treating these open transitions as the intermediate result
+% of the algorithm. After we get the intermediate results of open
+% transitions, we check them one by one.
+Here we declare first all the variables in the predicates, with their
+sorts.
+An example of syntax is::\\
+\centerline{$\OTvar{(declare-const\ |:ra:1:1|\ Action)}$}
+
+\noindent Then each term of the
+predicate is an assertion in Z3, as an example, in the former
+unsatisfiable result in Fig~\ref{schema:unsat-ot}, the contradiction is occurred in terms: \\
+\centerline{$\OTvar{(:ra:11:1=l)} \OTland \OTvar{(delta=:ra:11:1)}$}\\
+from which we generate the following two assertions:\\
+\centerline{$\OTvar{(assert\ (=\ |:ra:11:1|\ l))\ \ \ (assert\ (=\ delta\ |:ra:11:1|))}$}
+
+\noindent The predicate submitted to the Z3 also contains the
+assignments encodings.
+In the case of $ot_2$, it
+gives the assertion:\\
+\centerline{$\OTvar{assert (or (= var\_s0 0) (= var\_s0 01)))}$}
+
+\subsection{Simplification of Predicates}
+
+\subsection{Result of the running example}
+\label{section:full-result}
+
+\TODO{Update: we have 11 satisfiable OTs here}
+Our tool builds 30 open
+transitions, out of which 27 are detected unsatisfiable by Z3, we
+get only 3 results left; the resulting open automaton is shown in
+Fig. ~\ref{schema:lotos-result}, together with its open transitions.
+
+The resulting open transitions represent all the
+possible movements of the LOTOS example.
+What can be observed is any actions of the process $P$ from the beginning, until $P$ performs a $\delta(x)$ and the value of
+$x$ is transmitted to the $acc(x);Q$ giving out a silent action. Such behavior is performed by the $ot_1$ then $ot_2$. 
+Then it keeps presenting the behavior of $Q$, as seen in $ot_3$. 
+%The $ot_1$ transition means that the actions of the process $P$ could
+%be transmitted out, until $P$ performs a $\delta(x)$ and the value of
+%$x$ is transmitted, through transition
+%$ot_2$. The other 3 open transitions shows the behaviors of the
+%process $Q$ while the $ot_3$ and $ot_4$ won't be performed as the
+%controller has already set the value $s_0$ to 1 in the previous
+%action.
+
+\begin{figure}[t]
+   \centerline{\includegraphics[width=12cm]{XFIG/BIPresult-ArchFailureTimerMax}}
+   \caption{Open Automaton\TODO{syntax could be better...}}  \label{schema:resultOA}
+ \end{figure}
+
+\begin{figure}[h]
+%  \centerline{\includegraphics[width=5cm]{XFIG/LOTOSresult}}
+  \TODO{Detaisl of some OTs of the FailureTimer}
+
+$\begin{array}{@{}r@{}l@{}}
+    ot_1  = &\openrule{\{0 \xrightarrow{l}_{C_1} 0\}, ~~\{\xrightarrow{hb_{1}}_P\}, ~~[s_0=0 \!\land\! hb_{1} \neq \delta(x) \!\land\! v_1=hb_{1}]}
+    {\ostate{00} \xrightarrow{v_1} \ostate{00}}\\
+  \end{array}$
+
+$\begin{array}{@{}r@{}l@{}}
+    ot_2  = &\openrule{\{0 \xrightarrow{\delta}_{C_1} 0, 0 \xrightarrow{acc(x)}_{C_2} 1\}, ~~\{\xrightarrow{hb_{2}}_P\}, ~~[s_0=0 \!\land\!
+hb_{2}=\delta(x) \!\land\!
+v_2=\underline{\delta(x)}], ~~\{s_0 \xleftarrow{} 1\}}
+    {\ostate{00} \xrightarrow{v_2} \ostate{01}}\\
+  \end{array}$
+
+\caption{The open automaton of the LOTOS formula}  \label{schema:lotos-result}
+\end{figure}
+
+%\subsubsection{Result of CCS example}
+%\QIN{
+%also can present all the possible behavior of that CCS formula with 16 open
+%transitions in Fig. ~\ref{schema:ccs-result}, here we omitted the details of open transitions. 
+%In this example, there are 32 more transitions detected unsatisfiable by Z3.
+%}
+%
+%\QIN{
+%Here we only show one of the result transitions. It presents the value-passing between $a.P$ and $b.Q$ and they are synchronized then
+%give out an silent action $\tau$, process $P$ and $Q$ should not work in this case.
+%}
+%
+%\begin{figure}[h]
+%  \centerline{\includegraphics[width=5cm]{XFIG/CCSresult}}
+%  
+%  $\begin{array}{@{}r@{}l@{}}
+%    ot_1  = &\openrule{\{0 \xrightarrow{a}_{C_1} 1, 0 \xrightarrow{b}_{C_2} 1\}, ~~a=!ch_{11}(v_{11}) \!\land\! b=?ch_{11}(v_{11}) \!\land\! a\neq l \!\land\! b\neq r\!\land\! v_1=\tau}
+%    {\ostate{00} \xrightarrow{v_1} \ostate{11}}\\
+%  \end{array}$
+%  
+%\caption{The open automaton of the CCS parallel formula}  \label{schema:ccs-result}
+%\end{figure}
+
+%% \QIN{
+%% To sum up, from the pNets encoding the formulas of given algebra, which inputed by the user, we can exactly construct
+%% the open automaton for them. 
+%% }
+
+\section{Conclusion and Discussion}
+\label{section:conclusion}
+
+In this paper we presented the algorithm for generating an open
+automaton representing the semantics of an open pNet, and we described
+the implementation of the
+algorithm. Our implementation includes two main parts. First, we
+compute all the possible open transitions. The actions in pLTS and
+hole behaviors are composed in the algorithm while the generation of
+predicate need to match the combinations of the subnets with the
+synchronization vectors. Some of the open transitions obtained at this
+intermediate step, constructed in a structural manner from all
+possible combinations of possible logical predicates, may
+contain predicates which do not represent any possible concrete
+instantiations. 
+To get rid of these useless transitions, we use the SMT solver Z3 for checking the
+satisfiability of the predicate in each open transition. In
+order to do that, we encode into Z3 the action algebra presentation,
+the a representation of the predicates, before submitting them to the
+Z3 solver. We implemented our algorithm in the VerCors platform and use some
+running examples, encoding expressions from various process algebras, to test the
+algorithm. Our use-cases show that our encoding
+identifies successfully all unsatisfiable open transitions and that
+the resulting automaton reflects correctly the expected 
+movements of the encoded process expressions.
+
+Among the questions arising during this work, an important one is the
+efficiency of Z3 for our needs. Z3 is famous for being very fast for
+solving very large sets of assertions, and this could be important for
+us. But we encountered  some problems during the implementation the
+checking method using Z3. For example, if the $functions$ and the
+$datatypes$ part of the algebra presentation we submit to the solver
+are independent with each other, then checking the $assertions$ is a
+simple work. However, $functions$ on recursive $datatypes$ make it
+more complex, some special rules might be defined by user for the
+induction. Also, we need more evidence that dealing with more complex
+action algebras, that would involve axiomatizing their data structures
+into Z3 theories, will indeed allow us to decide validity of
+predicates.
+We may also try other automatic theorem provers, depending on the structure of the proofs we need.
+
+\TODO{Change perspective: we are working on the formal extensino of
+  BIB architectures, and their semantics in terms of pNets. Then
+  bisimulation and model-checking principles adapted to open pNet
+  systems are under development}
+
+Naturally, our next goals after the generation of the open automata
+will be to model-check, and to check equivalence of  pNets. While
+model-checking open automata (with a suitable logic including
+predicates on data) seems easy to define, equivalence checking is more challenging.
+In previous paper, we
+have already found the FH-bisimulation, inspired by~\cite{deSimone85} as a
+suitable definition. But usual approaches of bisimulation by partition
+refinement does not work easily with symbolic transitions. In a first
+step we may want instead to define and implement an algorithm for
+checking that a given equivalence relation between open automata 
+states is indeed a FH-Bisimulation. Finding automatically a
+bisimulation relation or the most general bisimulation will be more
+challenging. It appears also that when comparing different pNets with
+different structure, strong bisimulation will be too strong a notion,
+and that we will have to define proper notions of weak equivalence or
+refinements.
+
+Before that work, we need to reconsider the result open transitions
+from our algorithm. The ideal
+result that we showed in the bottom part of
+Fig.~\ref{schema:lotos-result} is not the one generated by the algorithm,
+because the original one contains many intermediate
+variables, such as fresh local variables of synchronization
+vectors, and fresh result variables of intermediate open transitions.
+Such intermediate variables come from the way predicates are
+generated, and depends on the particular structure of the pNet. But
+they are not significant in the resulting behavior, and should be
+eliminated before comparing such behavior with another pNet.
+To eliminate the intermediate variables in the predicate, we want to define
+the set of the significant variables that we won't eliminate: the
+local variables of pLTS transitions, the hole behaviors and the result
+action at the top level.
+The result of the elimination will be simpler predicates, that can be
+successfully compared (e.g. by Z3) within the bisimulation checking
+algorithm.
+
+\bibliographystyle{lncs/splncs}
+
+% \bibliography{oasis,biblio}
+\bibliography{biblio}
+
+% \newpage
+\appendix
+
+\section{More details on the generation algorithm}
+\subsection{Algebra specification}
+\subsection{Term algebra: type system and static semantics}
+Our models rely on a notion of parameterized actions, that are
+symbolic expressions using data types and variables. As our model aims
+at encoding the low-level behavior of possibly very different
+programming languages, we do not want to impose one specific algebra
+for denoting actions, nor any specific communication mechanism. So we
+leave unspecified the constructors of the algebra that will allow building
+expressions and actions. Moreover, we use a generic {\em action interaction}
+mechanism, based on unification between two or more action
+expressions. This will be used in the semantics of synchronization
+vectors to express various kinds of communication or synchronization mechanisms.
+
+\def\Talg{\mathcal{T}_{\Sigma,\P}}
+Formally, we assume the existence of a term algebra $\Talg$,
+where $\Sigma$ is the signature of the data and action constructors,
+and $\P$ a set of variables. Within $\Talg$, we distinguish a set of
+data expressions $\mathcal{E}_\P$, including a set of boolean
+expressions $\mathcal{B}_{\P}$ ($\mathcal{B}_{\P}\subseteq\mathcal{E}_\P$).
+On top of $\mathcal{E}_\P$ we build the action algebra
+$\mathcal{A}_\P$, with $\mathcal{A}_P\subseteq\mathcal{T}_\P,
+\mathcal{E}_P\cap\mathcal{A}_P=\emptyset$;
+naturally action terms will use data expressions as sub-terms.
+The function $\vars(t)$ identifies the set of variables in a term
+$t\in\AlgT$.
+
+pNets can encode naturally the notion of input actions as found e.g. in value-passing CCS
+\cite{Milner89} or of usual point-to-point message passing calculi, but it also allows
+for more general mechanisms, like gate negotiation in Lotos, or broadcast
+communications.
+
+\subsection{Fresh variables}
+
+%The variables in each synchronization vector are considered local, so
+%does the variables of an open transition such as its hole behaviors
+%and its result action. So we want rename the variables to make them
+%unique on every occurrence of a vector. Similarly, the name given to
+%the hole behaviors for each hole or the result action for each open
+%transition must be distinct. At the same time, we also hope them still
+%readable. Here we rename the variables with a regular format using the fresh function.
+
+Application of the semantic rules require generating a lot of fresh
+names, for different kind of variables. We could use a global name
+generator to guarantee unicity, but 
+at the same time, we also hope them still
+readable. Here we rename the variables with a regular format using the fresh function.
+More precisely, the fresh function generates a new name adding a
+suffix after the original name. The suffix contains three parts
+combined by a colon.
+
+\begin{definition}[Fresh variable]\label{fresh-variable}
+The format of \emph{fresh variable} (renaming) is defined as:
+``$\emph{prefix : tree\ index\ :\ counter}$''.
+\begin{itemize}
+   \item[$\bullet$] $prefix$ identifies the kind of the
+     variable. current kinds are: sva (SV action), ra (result action), hb (hole behavior).
+   \item[$\bullet$] $tree\ index$ is the index of the node containing the variable in the tree-like structure of the pNet.
+   \item[$\bullet$] $counter$ is the current value of the corresponding counter.
+\end{itemize}
+\end{definition}
+
+%\TODO{Option: Add the process and the vector ids ?}
+
+%$Prefix$ avoids the confusion between variables from different structures with the same name by attaching the type of the structure.
+$Tree\ index$ is given to every node of the pNets to mention which node the variable belongs to as pNets has a tree-like structure.
+To each node, the tree index is always a number sequence of the tree index of its higher level and the index of the node in this level at the last.
+$A\ set\ of\ counters$ is used to count the current times the SV, Hole, subnet invoked, or the number of possible OT generated to provide an identity.
+
+For example, in the running example, the first possible behavior of
+the hole, it doesn't have a name, only have the prefix ``hb''. The
+hole is the second subnets of the root node so its ``tree index'' is
+``12''. The fresh variable name is ``$\OTvar{:hb:12:1}$''. 
+\subsection{Variable managment}
+The variables in each synchronisation vector are considered local: for a given pNet expression, we must have fresh local variables for each occurrence of a vector (= each time we instantiate rule Tr2).
+Similarly the state variables of each copy of a given pLTS in the system, must be distinct, and those created for each application of Tr2 have to be fresh and all distinct.
+This will be implemented within the open-automaton generation algorithm, e.g.
+using name generation using a global counter as a suffix.
+\subsection{Filtering the behaviour combinations}
+\QIN{There is already able to filter some wrong open transitions during the matching.
+We can ensure that the synchronization vector is not matched with the subnets if there is only one side not involved.
+Then we can remove the transitions from the result of matching according to the condition $\gamma$ where
+$\gamma = \bigcup_{i\in I}(v_i\in\eta\land a'_i\in\eta)\lor(v_i\in\eta\land a'_i\in\eta) .$
+}
+\subsection{Translation to SMTlib input language}
 In order to submit satisfiability problems to Z3 (for the predicates
@@
 
-\subsubsection{Algebra presentations}
-
+\paragraph{Algebra presentations}
 \begin{definition}
@@
   \begin{itemize}
+    \item[]
     \item $Sorts_{CCS} = \{Action, Channel, Data, Int, Bool\}$
@@
 
-\begin{lstlisting}
+Then in pNet API these operators or constants (seemed as non-parameter operators) can be declared as:
+\begin{lstlisting}[basicstyle=\footnotesize\ttfamily, language=java, frame=single]
 AlgebraSort Action = new AlgebraSortImpl("Action");
@@
 
-\subsubsection{Expressions}
+\paragraph{Expressions}
 Once an algebra presentation is defined, we can construct expressions
@@
 \end{tabular}
-
-\paragraph{Presentation of algebra}
-
-\TODO{Improve this, inserting the main definition from the ``Checker'' document}
-%% Open pNet framework provides us
-%% with a model able to express the semantics of many different algebras
-%% or languages. In particular,
-As seen in section
-\ref{section:pnets}, the \emph{term algebra} used to express the
-action expressions and data parameters is left open in
-the pNet definition.
-
-So, for a given language, we now need to specify its data and action
-domains, giving them an abstract syntax (sorts, constructors, operators,
-and predicates). We call this a \emph{Presentation}.
-We also define a concrete syntax, that will be used for
-pretty-printing, but also for translating the presentation, and the
-predicates, into Z3 syntax (see the ``declare-datatypes'' statement in
-Fig~\ref{schema:smt-lib}).
-
-An algebra presentation contains:
-
-\begin{itemize}
-	\item Sorts: Constants sets of the algebra or types of the data
-          and actions (integer and boolean sort are implicitly
-          declared).  There \emph{must} be one sort for actions, and
-          eventually others for the types of data
-          parameters. In the LOTOS example, 
-          we have the $Action$ sort: $\OTvar{Action = } \{ l, \delta,
-          r, p, q, acc \} .$
-
-	\item Operators:
-          %Operators used to construct action expressions; they are
-          constructors and predicates for data and action sorts. For
-          instance, in our LOTOS example, we
-          have a generic action constructor ``$ACT$'', taking as
-          argument an action litteral and a data parameter, declared as:
-          $\OTvar{ACT:}\OTvar{< Action, Data >} \rightarrow \OTvar{Action.}$, 
-        \item Constants: The satisfiability solver need to know which
-          actions in the pLTS behaviors are constants (like the $l$, $\delta$, 
-          $r$ of the controllers in running example). 
-          For a given pNet system, the sort $Action$ will include all
-          these constants.
-\end{itemize}
-
-\paragraph{Interaction with Z3}
-%\TODO{1. example input of Z3 in SMT-LIB.[DONE] 2. software architecture.[DONE]}
-%There are several ways to interact with the Z3 solver. 
-%It is possible to use Z3 interactively using the SMT-LIB
-%(Python-based) language. 
-From inside our algorithm code, we submit satisfiability requests to
-Z3 using its JAVA API. Here for readability, we
-show the Z3 code using its SMT-LIB input language. As an
-example in
-Fig~\ref{schema:smt-lib}, we show the input for checking the
-transition of Fig.~\ref{schema:unsat-ot}. It contains the declaration
-of the LOTOS action algebra types 
-and constructors, then the declaration of variables, and finally the
-predicate to be checked, encoded as a set of assertions.
-%% Generally, some $datatypes$ are declared to input the sorts, while here
-%% we only declare one $datatypes$ named $Action$ to involve all the
-%% constant actions. Then we input the predicate of this open transition
-%% in two parts: the variables contained in the predicate are declared
-%% first, then the terms of predicate are inputed as $assertions$ one by
-%% one. 
-The result "unsat" in the output is just what we expected.
-
-%\TODO{edit the figure to make it smaller in height [DONE]}
-
-%We present the architecture of the interaction with Z3 in
-%Fig~\ref{schema:interaction}.
-%For each OT generated at the toplevel of a pNet, the predicate must be
-%submitted for satisfiability check to Z3. For that we need to
-%translate into Z3 (Java-API) syntax, both the elements of the action
-%algebra, and the predicates itself, including the encoding of the
-%variable assignments (the Post part).
-%
-%The $presentation$ of the action algebra
-%is declared at the beginning of the algorithm as the $sorts$ and the
-%$operators$ will be used throughout the whole algorithm. It is
-%translated into $datatypes$ and $functions$ then submitted to the Z3
-%at the same time. Each candidate predicate will then be translated
-%into $assertions$ before submitted to Z3 after the algorithm
-%computing out all the possible open transitions, they act as
-%intermediate results there. Together with the $datatypes$ and
-%$functions$, the $assertions$ are used to check the satisfiability of
-%the predicate in Z3.
-
-To build the input submitted to Z3 for each OT,
-we translate the algebra $presentation$, the predicates and the
-variable assignments (the Post part) into Z3 (Java-API) syntax.
-% The $presentation$ and the predicates are translated separately.
-
-\paragraph{Translation of Action algebra presentation}
-\TODO{Exerpt of the formalisation}
-The $datatypes$ are declared according to the $sorts$ the users
-declared in the $presentation$. If the return type of the $functions$
-is one of the $datatypes$, we add this $function$ to the $datatypes$ declaration.
-So when we declare the operator ACT we illustrated in section 4.1, it
-will be just declared together with the constants like :\\
-\centerline{$\OTvar{(ACT\ (action3\ Action)(data\ Int))}$}
-
-The $functions$ can also be declared independently, it usually applies to functions returning integer or boolean, in the format like:\\
-\centerline{$\OTvar{(declare\text{-}fun\ MAX\ (Int\ Int)\ Int)}$}
-
-%Although in Fig~\ref{schema:smt-lib} we have not declared $functions$ outside of $datatypes$, there still exists $functions$ declared independently.
-The input and output types of the $function$ are also determined by the construct of the  $operators$ in the presentation.
-For example, we define a new operator to present the equation between two actions in LOTOS example $\text{EQUAL}$ in the format likes:
-%
-%\[EQUAL: \quad < Action , Action > \rightarrow Bool .\]
-%
-%It will be translated into the Z3 statement: 
-%
-%\[\text{(declare-fun\ EQUAL\ (Action\ Action)\ Bool) .}\]
-
-\paragraph{Translating assignments into predicate terms}
-\TODO{Exerpt of the formalisation}
-
-%The assignments are also taken into account when checking the
-%satisfiability of the open transitions as they represent the value of
-%the variables involved in an OT. In order to do that, we employs a
-%translation from assignments into term of predicates. The assignments
-%required to be translated are only those belong to the variables
-%contain in the start states of the open transitions. The assignments
-%are represented as equations between the variables and the expressions
-%on the right side of assignment. For the assignments of the same
-%variable, we do not figure out which state is the precursor of current
-%state, we keep all these possible equations instead, and generate the
-%disjunction of these equations. The state could always move to the
-%target state if there exists one of the values of its variable
-%satisfies the guard.
-%%\TODO{It won't matter the variable of the next state
-%%except that the right hand side expression contain its variables. This
-%%is a problem left to be solved in our future work. WHICH PROBLEM ?}
-%After that, for the assignments of the different variables, we generate a conjunction of them. This way we obtain a new term of the predicate involving assignments of the variables.
-
-State-variable assignments are also treated as a part of the
-predicates when checking the satisfiability. % Here we need conduct some
-% translations,
-For each assignement in a $\Post$ predicate, such as $\{s_0 \leftarrow 1\}$ in section
-~\ref{section:op-semantics}, we translate it into an equation
-$s_0=1$. For several assignments of the same variable in the same state,
-we generate the disjunction of 
-these equations. Correspondingly, we generate a conjunction for the
-assignments from different variables.
-
-\paragraph{Checking satisfiability}
-
-% We check the satisfiability of open transitions on the top level of
-% the pNet, treating these open transitions as the intermediate result
-% of the algorithm. After we get the intermediate results of open
-% transitions, we check them one by one.
-Here we declare first all the variables in the predicates, with their
-sorts.
-An example of syntax is::\\
-\centerline{$\OTvar{(declare-const\ |:ra:1:1|\ Action)}$}
-
-\noindent Then each term of the
-predicate is an assertion in Z3, as an example, in the former
-unsatisfiable result in Fig~\ref{schema:unsat-ot}, the contradiction is occurred in terms: \\
-\centerline{$\OTvar{(:ra:11:1=l)} \OTland \OTvar{(delta=:ra:11:1)}$}\\
-from which we generate the following two assertions:\\
-\centerline{$\OTvar{(assert\ (=\ |:ra:11:1|\ l))\ \ \ (assert\ (=\ delta\ |:ra:11:1|))}$}
-
-\noindent The predicate submitted to the Z3 also contains the
-assignments encodings.
-In the case of $ot_2$, it
-gives the assertion:\\
-\centerline{$\OTvar{assert (or (= var\_s0 0) (= var\_s0 01)))}$}
-
-\subsection{Simplification of Predicates}
+\subsection{Elimination of intermediate variables}
 \QIN{
@@
 }
-
-\subsection{Result of the running example}
-\label{section:full-result}
-
-\TODO{Update: we have 11 satisfiable OTs here}
-Our tool builds 30 open
-transitions, out of which 27 are detected unsatisfiable by Z3, we
-get only 3 results left; the resulting open automaton is shown in
-Fig. ~\ref{schema:lotos-result}, together with its open transitions.
-
-The resulting open transitions represent all the
-possible movements of the LOTOS example.
-What can be observed is any actions of the process $P$ from the beginning, until $P$ performs a $\delta(x)$ and the value of
-$x$ is transmitted to the $acc(x);Q$ giving out a silent action. Such behavior is performed by the $ot_1$ then $ot_2$. 
-Then it keeps presenting the behavior of $Q$, as seen in $ot_3$. 
-%The $ot_1$ transition means that the actions of the process $P$ could
-%be transmitted out, until $P$ performs a $\delta(x)$ and the value of
-%$x$ is transmitted, through transition
-%$ot_2$. The other 3 open transitions shows the behaviors of the
-%process $Q$ while the $ot_3$ and $ot_4$ won't be performed as the
-%controller has already set the value $s_0$ to 1 in the previous
-%action.
-
-\begin{figure}[t]
-   \centerline{\includegraphics[width=12cm]{XFIG/BIPresult-ArchFailureTimerMax}}
-   \caption{Open Automaton\TODO{syntax could be better...}}  \label{schema:resultOA}
- \end{figure}
-
-\begin{figure}[h]
-%  \centerline{\includegraphics[width=5cm]{XFIG/LOTOSresult}}
-  \TODO{Detaisl of some OTs of the FailureTimer}
-
-$\begin{array}{@{}r@{}l@{}}
-    ot_1  = &\openrule{\{0 \xrightarrow{l}_{C_1} 0\}, ~~\{\xrightarrow{hb_{1}}_P\}, ~~[s_0=0 \!\land\! hb_{1} \neq \delta(x) \!\land\! v_1=hb_{1}]}
-    {\ostate{00} \xrightarrow{v_1} \ostate{00}}\\
-  \end{array}$
-
-$\begin{array}{@{}r@{}l@{}}
-    ot_2  = &\openrule{\{0 \xrightarrow{\delta}_{C_1} 0, 0 \xrightarrow{acc(x)}_{C_2} 1\}, ~~\{\xrightarrow{hb_{2}}_P\}, ~~[s_0=0 \!\land\!
-hb_{2}=\delta(x) \!\land\!
-v_2=\underline{\delta(x)}], ~~\{s_0 \xleftarrow{} 1\}}
-    {\ostate{00} \xrightarrow{v_2} \ostate{01}}\\
-  \end{array}$
-
-\caption{The open automaton of the LOTOS formula}  \label{schema:lotos-result}
-\end{figure}
-
-%\subsubsection{Result of CCS example}
-%\QIN{
-%also can present all the possible behavior of that CCS formula with 16 open
-%transitions in Fig. ~\ref{schema:ccs-result}, here we omitted the details of open transitions. 
-%In this example, there are 32 more transitions detected unsatisfiable by Z3.
-%}
-%
-%\QIN{
-%Here we only show one of the result transitions. It presents the value-passing between $a.P$ and $b.Q$ and they are synchronized then
-%give out an silent action $\tau$, process $P$ and $Q$ should not work in this case.
-%}
-%
-%\begin{figure}[h]
-%  \centerline{\includegraphics[width=5cm]{XFIG/CCSresult}}
-%  
-%  $\begin{array}{@{}r@{}l@{}}
-%    ot_1  = &\openrule{\{0 \xrightarrow{a}_{C_1} 1, 0 \xrightarrow{b}_{C_2} 1\}, ~~a=!ch_{11}(v_{11}) \!\land\! b=?ch_{11}(v_{11}) \!\land\! a\neq l \!\land\! b\neq r\!\land\! v_1=\tau}
-%    {\ostate{00} \xrightarrow{v_1} \ostate{11}}\\
-%  \end{array}$
-%  
-%\caption{The open automaton of the CCS parallel formula}  \label{schema:ccs-result}
-%\end{figure}
-
-%% \QIN{
-%% To sum up, from the pNets encoding the formulas of given algebra, which inputed by the user, we can exactly construct
-%% the open automaton for them. 
-%% }
-
-\section{Conclusion and Discussion}
-\label{section:conclusion}
-
-In this paper we presented the algorithm for generating an open
-automaton representing the semantics of an open pNet, and we described
-the implementation of the
-algorithm. Our implementation includes two main parts. First, we
-compute all the possible open transitions. The actions in pLTS and
-hole behaviors are composed in the algorithm while the generation of
-predicate need to match the combinations of the subnets with the
-synchronization vectors. Some of the open transitions obtained at this
-intermediate step, constructed in a structural manner from all
-possible combinations of possible logical predicates, may
-contain predicates which do not represent any possible concrete
-instantiations. 
-To get rid of these useless transitions, we use the SMT solver Z3 for checking the
-satisfiability of the predicate in each open transition. In
-order to do that, we encode into Z3 the action algebra presentation,
-the a representation of the predicates, before submitting them to the
-Z3 solver. We implemented our algorithm in the VerCors platform and use some
-running examples, encoding expressions from various process algebras, to test the
-algorithm. Our use-cases show that our encoding
-identifies successfully all unsatisfiable open transitions and that
-the resulting automaton reflects correctly the expected 
-movements of the encoded process expressions.
-
-Among the questions arising during this work, an important one is the
-efficiency of Z3 for our needs. Z3 is famous for being very fast for
-solving very large sets of assertions, and this could be important for
-us. But we encountered  some problems during the implementation the
-checking method using Z3. For example, if the $functions$ and the
-$datatypes$ part of the algebra presentation we submit to the solver
-are independent with each other, then checking the $assertions$ is a
-simple work. However, $functions$ on recursive $datatypes$ make it
-more complex, some special rules might be defined by user for the
-induction. Also, we need more evidence that dealing with more complex
-action algebras, that would involve axiomatizing their data structures
-into Z3 theories, will indeed allow us to decide validity of
-predicates.
-We may also try other automatic theorem provers, depending on the structure of the proofs we need.
-
-\TODO{Change perspective: we are working on the formal extensino of
-  BIB architectures, and their semantics in terms of pNets. Then
-  bisimulation and model-checking principles adapted to open pNet
-  systems are under development}
-
-Naturally, our next goals after the generation of the open automata
-will be to model-check, and to check equivalence of  pNets. While
-model-checking open automata (with a suitable logic including
-predicates on data) seems easy to define, equivalence checking is more challenging.
-In previous paper, we
-have already found the FH-bisimulation, inspired by~\cite{deSimone85} as a
-suitable definition. But usual approaches of bisimulation by partition
-refinement does not work easily with symbolic transitions. In a first
-step we may want instead to define and implement an algorithm for
-checking that a given equivalence relation between open automata 
-states is indeed a FH-Bisimulation. Finding automatically a
-bisimulation relation or the most general bisimulation will be more
-challenging. It appears also that when comparing different pNets with
-different structure, strong bisimulation will be too strong a notion,
-and that we will have to define proper notions of weak equivalence or
-refinements.
-
-Before that work, we need to reconsider the result open transitions
-from our algorithm. The ideal
-result that we showed in the bottom part of
-Fig.~\ref{schema:lotos-result} is not the one generated by the algorithm,
-because the original one contains many intermediate
-variables, such as fresh local variables of synchronization
-vectors, and fresh result variables of intermediate open transitions.
-Such intermediate variables come from the way predicates are
-generated, and depends on the particular structure of the pNet. But
-they are not significant in the resulting behavior, and should be
-eliminated before comparing such behavior with another pNet.
-To eliminate the intermediate variables in the predicate, we want to define
-the set of the significant variables that we won't eliminate: the
-local variables of pLTS transitions, the hole behaviors and the result
-action at the top level.
-The result of the elimination will be simpler predicates, that can be
-successfully compared (e.g. by Z3) within the bisimulation checking
-algorithm.
-
-\bibliographystyle{lncs/splncs}
-
-% \bibliography{oasis,biblio}
-\bibliography{biblio}
-
-% \newpage
-\appendix
-
-\section{More details on the generation algorithm}
-\subsection{Algebra specification}
-\subsection{Term algebra: type system and static semantics}
-\subsection{Fresh variables}
-
-%The variables in each synchronization vector are considered local, so
-%does the variables of an open transition such as its hole behaviors
-%and its result action. So we want rename the variables to make them
-%unique on every occurrence of a vector. Similarly, the name given to
-%the hole behaviors for each hole or the result action for each open
-%transition must be distinct. At the same time, we also hope them still
-%readable. Here we rename the variables with a regular format using the fresh function.
-
-Application of the semantic rules require generating a lot of fresh
-names, for different kind of variables. We could use a global name
-generator to guarantee unicity, but 
-at the same time, we also hope them still
-readable. Here we rename the variables with a regular format using the fresh function.
-More precisely, the fresh function generates a new name adding a
-suffix after the original name. The suffix contains three parts
-combined by a colon.
-
-\begin{definition}[Fresh variable]\label{fresh-variable}
-The format of \emph{fresh variable} (renaming) is defined as:
-``$\emph{prefix : tree\ index\ :\ counter}$''.
-\begin{itemize}
-   \item[$\bullet$] $prefix$ identifies the kind of the
-     variable. current kinds are: sva (SV action), ra (result action), hb (hole behavior).
-   \item[$\bullet$] $tree\ index$ is the index of the node containing the variable in the tree-like structure of the pNet.
-   \item[$\bullet$] $counter$ is the current value of the corresponding counter.
-\end{itemize}
-\end{definition}
-
-%\TODO{Option: Add the process and the vector ids ?}
-
-%$Prefix$ avoids the confusion between variables from different structures with the same name by attaching the type of the structure.
-$Tree\ index$ is given to every node of the pNets to mention which node the variable belongs to as pNets has a tree-like structure.
-To each node, the tree index is always a number sequence of the tree index of its higher level and the index of the node in this level at the last.
-$A\ set\ of\ counters$ is used to count the current times the SV, Hole, subnet invoked, or the number of possible OT generated to provide an identity.
-
-For example, in the running example, the first possible behavior of
-the hole, it doesn't have a name, only have the prefix ``hb''. The
-hole is the second subnets of the root node so its ``tree index'' is
-``12''. The fresh variable name is ``$\OTvar{:hb:12:1}$''. 
-\subsection{Variable managment}
-\subsection{Filtering the behaviour combinations}
-\subsection{Translation to SMTlib input language}
-\subsection{Elimination of intermediate variables}
-
 \section{Full examples}

### 2018-01-12 2017-Xudong-SMT/FM-2018-extended.tex
eric

--- 2018-01-12 2017-Xudong-SMT/FM-2018-extended.tex
@@
   between INRIA and ECNU, Shanghai}}
-\author{ Xudong Qin\inst{2,3}  \ \ \  Eric Madelaine\inst{1,2}
-  \ \ \  Min Zhang\inst{3}} 
-\institute{Univ. of Nice Sophia Antipolis, CNRS, UMR 7271, 06900 Sophia Antipolis, France
-	\and INRIA Sophia Antipolis M\'edit\'erann\'ee, BP 93, 06902 Sophia Antipolis, France
-\and Shanghai Key Laboratory of Trustworthy Computing, ECNU, China}
+\author{ Xudong Qin\inst{1,2}  \ \ \  Simon Bliudze\inst{3} \ \ \ Eric Madelaine\inst{1}
+  \ \ \  Min Zhang\inst{2}} 
+\institute{Universit\'e C\^ote d'Azur, Inria, CNRS, I3S, 06902 Sophia Antipolis, France
+        \and Shanghai Key Laboratory of Trustworthy Computing, ECNU, China
+\and INRIA Lille }
 \date{}                                           % Activate to display a given date or no date
@@
 \begin{abstract}
-  \TODO{not good for a FM, (to be rewriten by Eric)}
-
-  Open pNets are used to model the behavior of open
-  synchronous or asynchronous systems expressed in various calculi
-  or languages. They are endowed with a symbolic operational semantics
-  in terms of so-called ``Open Automata''. We implement an algorithm
-  computing this semantics, and building predicates expressing the
-  synchronization conditions allowing some combination of events in
-  the pNet system. Checking such predicates requires symbolic
-  reasoning over first order logics, and specific functions of each
-  action algebra. To reduce the complexity of the generated open
-  automata, we use the Z3 SMT engine to check satisfiability of the
-  predicates, and minimize the number of significant symbolic
-  transitions.
+Open pNets are used to model the behavior of open systems, both
+synchronous or asynchronous, expressed in various calculi or
+languages. They are endowed with a symbolic operational semantics in
+terms of so-called ``Open Automata''. This allows to check properties of
+such systems in a compositionnal manner. 
+We implement an algorithm computing this semantics,
+building predicates expressing the synchronization conditions
+between the events of the pNet sub-systems. Checking such
+predicates requires symbolic reasoning over first order logics, but
+also over application-specific data. We use the Z3 SMT engine to check
+satisfiability of the predicates, and prune the open automaton of its
+unsatisfiable transitions.
+As an industrial oriented use-case, we use so-called "architectures"
+of BIP systems, that have been used to specify the control software of
+ESA microsatellites. We use pNets to encode BIP architectures,
+extended with explicite data in synchronisations, and we compute their
+open automaton semantics. Cet automate peut alors être utilisé pour
+monter les propriétés comme, \TODO{ par exemple ..}
 
@@
 
-%The preceding definition relies on the auxiliary functions below:
-
-%\begin{definition}[Sorts, Holes, Leaves of pNets]
-%  \begin{itemize}
-%  \item The sort of a pNet is its signature, i.e. the set of actions it can
-%perform. In the definition of sorts, we do not need to distinguish
-%input variables (that specify the dataflow within LTSs), so for
-%computing LTS sorts, we use a substitution operator\footnote{$\subst{y_k\gets x_k}^{k\in K}$ is the parallel substitution 
-%operation.} to remove the
-%\emph{input marker} of variables. Formally:
-%\[
-%\begin{array}{l}
-%\Sort(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{x \gets ?x| 
-%x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
-%		J}\rangle} s'\in \to \} \\ \Sort(\mylangle
-%\set{\pNet}, \set{\symb{S}}, \set{\symb{SV}}\myrangle) =\{\alpha'_k |\, \alpha_j^{j\in J_k}\to\alpha'_k\in\set{\symb{SV}}\}
-%\end{array}
-%\]
-%
-%\item
-%The set of holes of a pNet is defined inductively; the sets of holes
-%in a pNet node and its subnets are all disjoint:
-%  \[\begin{array}{l}
-%\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset \\
-%\Holes(\mylangle \pNet_i^{i\in I}\!,S_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) =J\cup{\displaystyle \bigcup_{i\in I}\Holes(\pNet_i)}\\
-%\forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
-%\forall i_1,i_2\in I.\,i_1\neq i_2\Rightarrow  \Holes(\pNet_{i_1})\cap\Holes(\pNet_{i_2})=\emptyset
-%\end{array}\]
-%\item
-%The set of leaves of a pNet is the set of all pLTSs occurring in the structure, defined inductively as:
-%\[\begin{array}{l}
-%\Leaves(\mylangle S,s_0, \to\myrangle) \!=\! \{ \mylangle S,s_0, \to\myrangle \}\\
-%\Leaves(\mylangle \pNet_i^{i\in I}\!,S_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \bigcup_{i\in I}\Leaves(\pNet_i)}
-%\end{array}\]
-%\end{itemize}
-%\end{definition}
-%
-%A pNet $Q$ is \emph{closed} if it has no hole: $\Holes(Q)=\emptyset$; else it
-%is said to be \emph{open}.
-
-%% \begin{figure}[t]
-%% \begin{minipage}{6.1cm}
-
-%%   \includegraphics[width=\linewidth]{XFIG/Enable1}
-%%   \\[1.3ex]
-%%  \includegraphics[width=\linewidth]{XFIG/Enable2}
-%%   \caption{Two pNet encodings for  Enable }  \label{schema:enable-pnets}
-%% \end{minipage}
-%%   \hspace{2mm}
-%% \begin{minipage}{6cm}
-%%   \includegraphics[width=\linewidth]{XFIG/P-QR}
-%%   \caption{Composed pNet for ``P>>(Q>>R)''}  \label{schema:enable-composed}
-%% \end{minipage}
-
-%% \end{figure}
-
 \section{BIP architectures, and their encodings into pNets}
 \label{section:BIParchitectures}
+\TODO{Simon: can you do this in less than one page ? If you prefer,
+  merge with ``Running example'' may be easier to describe the syntax}
 
@@
 \label{section:FailureTimerMax}
-
-Several publications \cite{HMZ:PDP15,henrio:Forte2016} already have introduced
-many examples of pNets, encoding
-operators of various classical process algebras, or more complex
-synchronization structures in distributed or parallel languages.
+\TODO{1.5 page including figures ?}
+
+%% Several publications \cite{HMZ:PDP15,henrio:Forte2016} already have introduced
+%% many examples of pNets, encoding
+%% operators of various classical process algebras, or more complex
+%% synchronization structures in distributed or parallel languages.
+
+\TODO{Should have here both the original BIP drawing (Simon), and the
+  pNet encoding (fig by Eric)}
 
@@
 \end{array}\]
-%% In any other case (if the action families do not match or if there is no valuation of
-%% variables such that the above formula can be ensured) the predicate is undefined.
 
@@
 
-%\begin{example}\emph{An open-transition.}
-%  \label{OT:lotos-composed}
+\begin{example}\emph{An open-transition.}
+  \label{OT:lotos-composed}
 %
@@
 %     {\ostate{00} \xrightarrow{\underline{\delta(x)}} \ostate{01}}$
-%\end{example}
+\end{example}
 %
@@
 \paragraph{Structural Semantic Rules:}
+\TODO{Do we push the rules in the appendix, and leave only a short high
+  level desciption here ?}
+
 Now we build the semantics of an open pNet as an open automaton where
@@
 
-%\paragraph{Fresh variables management.}
-
-% This will be implemented within the open-automaton generation algorithm,
-% e.g. using name generation using a global counter as a suffix.
-
-% \TODO{To be move  by Xudong}
-
-%\subsection{Presentation of algebra}
-%One of the important goal of the Open pNet framework is to provide us
-%with a model able to express the semantics of many different algebras
-%or languages. In particular, as we have seen in section
-%\ref{section:pnets}, the \emph{term algebra} used to express the
-%action expressions and the data in their parameters is left open in
-%the pNet formalization.
-%
-%So, for a given language, we now need to specify its data and action
-%domains, giving them an abstract syntax (sorts, constructors, operators,
-%and predicates). We call this a \emph{Presentation}.
-%We also define a concrete syntax, that will be used for
-%pretty-printing, but also for translating the presentation, and the
-%predicates, into Z3 syntax (we shall detail this translation in
-%section \ref{section:pruning}).
-%
-%An algebra presentation contains:
-%\begin{itemize}
-%	\item Sorts: Constants sets of the algebra or types of the data
-%          and actions. In every presentation, sorts for integer and
-%          boolean are implicitly declared.  There \emph{must} be one sort for actions, and eventually 
-%several others for the types of data parameters. In the LOTOS example,
-%we have the $Action$ sort: $\OTvar{Action = } \{ l, \delta, r, p, q, acc \} .$
-%
-%	\item Operators: Operators used to construct action
-%          expressions (including their data parameters); they are
-%          constructors of data and action sorts, but also predicates
-%          over these objects. For instance, in our LOTOS example, we
-%          could have two constructor functions ``$DELTA$'' and ``$ACC$''
-%          to construct the action expression $\delta(x)$ and $acc(x)$, declared as:
-%          $\OTvar{DELTA:}\OTvar{< Data >} \rightarrow \OTvar{Action .}$
-%        \item Constants: The satisfiability solver need to know which
-%          actions in the pLTS behaviors are constants (like the $l$, $\delta$, 
-%          $r$ of the controllers in running example). 
-%          For a given pNet system, a sort $Action$ will include all
-%          these constants.
-%\end{itemize}
-
-%We need introduce operators for building expressions, of both action
-%and data sorts, when encoding the 
-%algebra into pNets. So that is needed to know about the input and
-%output of the operators used in the expressions from those
-%algebra. The input and output should belong to the sorts of the
-%pNet. When there are $k$ sorts in this pNet, the structure of a
-%$n$-ary operator is vector as $< Sort_{i_1}, ... , Sort_{i_n} >
-%\rightarrow Sort_j , i_1 , ... , i_n, j \in [0..k] $.
-%% We  introduce operators for building expressions, either action
-%% expressions or predicate terms, when encoding the algebra into
-%% pNets. The operators here are treated as functions, with the sorts of
-%% the pNet acting as the types of their input and output. 
-%% For instance, in our LOTOS running example, we use a function ``$ACT$'' action to construct the action expression $\delta(x)$ and $acc(x)$.
-We can define the operator as a binary operator with the format like:
-
-%%  \[\OTvar{ACT:}\OTvar{< Action, Int >} \rightarrow \OTvar{Action .} \]
-
-%\paragraph{Implementation of the expression meta-model}
-% \TODO{maybe we could remove this paragraph (and the figure)}
-%The VerCors platform uses Ecore and EMF to define the structure of
-%both pNets and actions algebras. There exists a predefined set of
-%action and data expressions classes, including boolean, integer and
-%action expressions, with predefined variables, literal (constants),
-%and operators. Operators can be categorized into unary, binary and
-%N-ary operators.
-%The original version of VerCors did not allow to extend these classes,
-%we have modified its architecture so that a user can extend them,
-%defining more elements for his specific algebra.
-%
-%In Fig~\ref{schema:expression-pnets}, we show the Expression class we
-%improved, including extensions for CCS and LOTOS.
-%
-%\begin{figure}[t]
-%  \includegraphics[width=\linewidth]{XFIG/Expression}
-%  \caption{The architecture of Expression class}  \label{schema:expression-pnets}
-%\end{figure}
-
-%\TODO{give an example of user-defined sorts/operators, and tell that
-%  you will give it's translation into Z3 in section 5.4}
-
-% \TODO{To be move / replace by Xudong}
-
-%\subsection{Computing and using open automata}
-%In this section we present an algorithm to construct the open
-%automaton representing the behavior of an open pNet, and show
-%under which conditions this automaton is finite.
-%
-%\begin{alg}[behavioral semantics of open pNets: Sketch]
-%This is a standard residual algorithm over a set of open-automaton
-%states, but where transitions are open transitions
-%constructively ``proven'' by deduction trees.
-%
-%1) Start with a set of unexplored states containing the initial state
-%of the automaton, and an empty set of explored states.
-%
-%2) While there are unexplored states:
-%
-%2a) pick one state from the unexplored set and add it to the explored
-%set. From this state
-%build all possible deduction trees by application of the structural
-%rules Tr1 and Tr2, using all applicable combinations
-%of synchronization vectors.
-%
-%2b) For each deduction trees, extract the resulting
-%open-transition.
-%Its predicate is checked (using Z3) for  satisfiability. If it is
-%unsatisfiable, the resulting OT is discarded. This will minimize the
-%number of resulting transitions. 
-%
-%2c) For each open-transition,  add the transition in the outgoing transitions of
-%the current state, and add the
-%resulting state in the unexplored set if it is not already in the
-%explored set.
-%
-%3) Finally a reachability check could potentially
-%prune the state space.
-%
-%\end{alg}
-
-%% \TODO{ERIC: after we move / replace Algoriithm 1, this will not make sense any longer. I will replace it with a more informal paragraph, in section 5}
-
-%% To have some practical interest, it is important to know when this
-%% algorithm terminates. The following theorem shows that an open-pNet
-%% with finite synchronization sets, finitely many leaves and
-%% holes, and each pLTS at leaves having a finite number of states and
-%% (symbolic) transitions, has a finite automaton. The proof can be found
-%% in \cite{henrio:Forte2016}.
-
-%% \begin{theorem}[Finiteness of open-automata.]\\
-%% Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
-%%   J}$, if the sets $L$ and $J$ are finite, if the synchronization vectors of all pNets 
-%%   included in  $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ 
-%%   are finite, and if
-%% $\forall i \in L.\, finite{(states(pLTS_i))} \text{ and } pLTS_i$
-%% has a finite number of state variables, then Algorithm 1 terminates
-%% and produces an open automaton 
-%% $\mathcal{T}$ with finitely many states and transitions.
-
-% Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in
-%     K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
-%   J}$,
-% build its semantics as in algorithm 1.
-
-% We have:
-
-% $$ finite{(L)} \land finite{(J)} \land \forall i \in L finite{(\{s_i\})}
-%   \to finite{(\mathcal{T})}$$
-% \end{theorem}
-
 \section{Implementation}
@@
 \subsection{Simplification of Predicates}
+\TODO{[Eric]: Motivate, and refs  -- reduce the section here to approx
+  half a page} 
 \QIN{
@@
 \section{More details on the generation algorithm}
+
+%\paragraph{Fresh variables management.}
+
+% This will be implemented within the open-automaton generation algorithm,
+% e.g. using name generation using a global counter as a suffix.
+
+% \TODO{To be move  by Xudong}
+
+%\subsection{Presentation of algebra}
+%One of the important goal of the Open pNet framework is to provide us
+%with a model able to express the semantics of many different algebras
+%or languages. In particular, as we have seen in section
+%\ref{section:pnets}, the \emph{term algebra} used to express the
+%action expressions and the data in their parameters is left open in
+%the pNet formalization.
+%
+%So, for a given language, we now need to specify its data and action
+%domains, giving them an abstract syntax (sorts, constructors, operators,
+%and predicates). We call this a \emph{Presentation}.
+%We also define a concrete syntax, that will be used for
+%pretty-printing, but also for translating the presentation, and the
+%predicates, into Z3 syntax (we shall detail this translation in
+%section \ref{section:pruning}).
+%
+%An algebra presentation contains:
+%\begin{itemize}
+%	\item Sorts: Constants sets of the algebra or types of the data
+%          and actions. In every presentation, sorts for integer and
+%          boolean are implicitly declared.  There \emph{must} be one sort for actions, and eventually 
+%several others for the types of data parameters. In the LOTOS example,
+%we have the $Action$ sort: $\OTvar{Action = } \{ l, \delta, r, p, q, acc \} .$
+%
+%	\item Operators: Operators used to construct action
+%          expressions (including their data parameters); they are
+%          constructors of data and action sorts, but also predicates
+%          over these objects. For instance, in our LOTOS example, we
+%          could have two constructor functions ``$DELTA$'' and ``$ACC$''
+%          to construct the action expression $\delta(x)$ and $acc(x)$, declared as:
+%          $\OTvar{DELTA:}\OTvar{< Data >} \rightarrow \OTvar{Action .}$
+%        \item Constants: The satisfiability solver need to know which
+%          actions in the pLTS behaviors are constants (like the $l$, $\delta$, 
+%          $r$ of the controllers in running example). 
+%          For a given pNet system, a sort $Action$ will include all
+%          these constants.
+%\end{itemize}
+
+%We need introduce operators for building expressions, of both action
+%and data sorts, when encoding the 
+%algebra into pNets. So that is needed to know about the input and
+%output of the operators used in the expressions from those
+%algebra. The input and output should belong to the sorts of the
+%pNet. When there are $k$ sorts in this pNet, the structure of a
+%$n$-ary operator is vector as $< Sort_{i_1}, ... , Sort_{i_n} >
+%\rightarrow Sort_j , i_1 , ... , i_n, j \in [0..k] $.
+%% We  introduce operators for building expressions, either action
+%% expressions or predicate terms, when encoding the algebra into
+%% pNets. The operators here are treated as functions, with the sorts of
+%% the pNet acting as the types of their input and output. 
+%% For instance, in our LOTOS running example, we use a function ``$ACT$'' action to construct the action expression $\delta(x)$ and $acc(x)$.
+We can define the operator as a binary operator with the format like:
+
+%%  \[\OTvar{ACT:}\OTvar{< Action, Int >} \rightarrow \OTvar{Action .} \]
+
+%\paragraph{Implementation of the expression meta-model}
+% \TODO{maybe we could remove this paragraph (and the figure)}
+%The VerCors platform uses Ecore and EMF to define the structure of
+%both pNets and actions algebras. There exists a predefined set of
+%action and data expressions classes, including boolean, integer and
+%action expressions, with predefined variables, literal (constants),
+%and operators. Operators can be categorized into unary, binary and
+%N-ary operators.
+%The original version of VerCors did not allow to extend these classes,
+%we have modified its architecture so that a user can extend them,
+%defining more elements for his specific algebra.
+%
+%In Fig~\ref{schema:expression-pnets}, we show the Expression class we
+%improved, including extensions for CCS and LOTOS.
+%
+%\begin{figure}[t]
+%  \includegraphics[width=\linewidth]{XFIG/Expression}
+%  \caption{The architecture of Expression class}  \label{schema:expression-pnets}
+%\end{figure}
+
+%\TODO{give an example of user-defined sorts/operators, and tell that
+%  you will give it's translation into Z3 in section 5.4}
+
+% \TODO{To be move / replace by Xudong}
+
+%\subsection{Computing and using open automata}
+%In this section we present an algorithm to construct the open
+%automaton representing the behavior of an open pNet, and show
+%under which conditions this automaton is finite.
+%
+%\begin{alg}[behavioral semantics of open pNets: Sketch]
+%This is a standard residual algorithm over a set of open-automaton
+%states, but where transitions are open transitions
+%constructively ``proven'' by deduction trees.
+%
+%1) Start with a set of unexplored states containing the initial state
+%of the automaton, and an empty set of explored states.
+%
+%2) While there are unexplored states:
+%
+%2a) pick one state from the unexplored set and add it to the explored
+%set. From this state
+%build all possible deduction trees by application of the structural
+%rules Tr1 and Tr2, using all applicable combinations
+%of synchronization vectors.
+%
+%2b) For each deduction trees, extract the resulting
+%open-transition.
+%Its predicate is checked (using Z3) for  satisfiability. If it is
+%unsatisfiable, the resulting OT is discarded. This will minimize the
+%number of resulting transitions. 
+%
+%2c) For each open-transition,  add the transition in the outgoing transitions of
+%the current state, and add the
+%resulting state in the unexplored set if it is not already in the
+%explored set.
+%
+%3) Finally a reachability check could potentially
+%prune the state space.
+%
+%\end{alg}
+
+%% \TODO{ERIC: after we move / replace Algoriithm 1, this will not make sense any longer. I will replace it with a more informal paragraph, in section 5}
+
+%% To have some practical interest, it is important to know when this
+%% algorithm terminates. The following theorem shows that an open-pNet
+%% with finite synchronization sets, finitely many leaves and
+%% holes, and each pLTS at leaves having a finite number of states and
+%% (symbolic) transitions, has a finite automaton. The proof can be found
+%% in \cite{henrio:Forte2016}.
+
+%% \begin{theorem}[Finiteness of open-automata.]\\
+%% Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
+%%   J}$, if the sets $L$ and $J$ are finite, if the synchronization vectors of all pNets 
+%%   included in  $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ 
+%%   are finite, and if
+%% $\forall i \in L.\, finite{(states(pLTS_i))} \text{ and } pLTS_i$
+%% has a finite number of state variables, then Algorithm 1 terminates
+%% and produces an open automaton 
+%% $\mathcal{T}$ with finitely many states and transitions.
+
+% Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in
+%     K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
+%   J}$,
+% build its semantics as in algorithm 1.
+
+% We have:
+
+% $$ finite{(L)} \land finite{(J)} \land \forall i \in L finite{(\{s_i\})}
+%   \to finite{(\mathcal{T})}$$
+% \end{theorem}
+
 \subsection{Algebra specification}

### 2018-01-13 2017-Xudong-SMT/FM-2018-extended.tex

@@
 
+\TODO{Eric: merge term algebra, algebra pres, and add a short example (BIP)}
+
 \paragraph*{Term algebra.}
@@
   merge with ``Running example'' may be easier to describe the syntax}
+
+\TODO{Simon: or may be better, present BIP architectures and the use-case \_BEFORE\_ The pNets definition, and define the encoding here}
 
@@
 
-\section{Implementation}
+\section{Generation of Open Automata}
 \label{section:implementation}
-The VerCors platform uses pNets as the intermediate language
-for some high-level language or graphical formalism to be translated
-into both input for a model-checker and for generating executable code
-automatically \cite{HKM-FASE16}.
-We have extended the pNet API in VerCors to deal with open pNets, and
-also to specify the structure of action algebras.
+
+\TODO{Eric: add a header, reorganise the parts of the algorithm}
 
@@
 
-%\begin{algorithm}
-%\caption{Open Automaton Generation}
-%\begin{algorithmic}[1]
-%
-%\State Initialize sets $U$, $E$ for unexplored/explored global states
-%$U$, $L$ for result OTs;
-%\While{!isEmpty(U)}
-%	\State Chose a global state $S$ in $U$; recursively applying Tr1 or Tr2 on the root node;
-%	\If{Subnet is a pLTS}
-%                \State Get the local state of the pLTS $s$ from $S$;
-%		\For{each transition $tr$ starting from $s$} Apply Tr1
-%			\State Build the corresponding
-%                        $OT$; store $OT$ in $L$; 
-%                 \EndFor
-%	\EndIf
-%	\If{Subnet is a pNet}
-%		\For{each $sv \in SV$} Apply Tr2
-%			\State Invoke $Combining()$ to generate the
-%                        combination of sub-transitions, $Matching()$
-%                        to match the combination with the $sv$; Store the result OTs in $L$; 
-%		\EndFor
-%	\EndIf
-%	\For{each target global state $T$ from $OT \in L$}
-%		\IfThen{$(!U.contains(T))\ \&\&\ (!E.contains(T))$}{Add $T$ into the $U$;}
-%	\EndFor
-%\EndWhile
-%\State Prune the open transitions in $L$ using the SMT solver;
-%\State \Return $L$;
-%
-%\end{algorithmic}  
-%\end{algorithm}
+\TODO{Eric: rewrite}
+We have already have the sketch of computing the open automata \cite{???}.
+While in our implementation we does not build explicitly a proof tree for every open transition.
+Instead, we repeat applying the Tr1 or Tr2 to generate the sub-transitions.
+Tr1 is applied on the leaf (pLTS) simply take the pLTS transitions through the given start state and add the predicate in pNet to generate the open transition.
+When applying Tr2 we use two methods, combining and matching, to generate the new predicate of the open transitions in a hierarchical manner
+as in this case the composition the subnets brings more constraints for synchronizing behaviors. 
+Beside the new generated predicate, the predicates from the subnets are also added as a conjunction with those new predicates.
 
@@
 
-\subsection{The Generation of Open Automata}
-
-\QIN{
-We have already have the sketch of computing the open automata \cite{???}.
-While in our implementation we does not build explicitly a proof tree for every open transition.
-Instead, we repeat applying the Tr1 or Tr2 to generate the sub-transitions.
-Tr1 is applied on the leaf (pLTS) simply take the pLTS transitions through the given start state and add the predicate in pNet to generate the open transition.
-When applying Tr2 we use two methods, combining and matching, to generate the new predicate of the open transitions in a hierarchical manner
-as in this case the composition the subnets brings more constraints for synchronizing behaviors. 
-Beside the new generated predicate, the predicates from the subnets are also added as a conjunction with those new predicates.
-}
-
 %Algorithm 1 shows the main structure of the algorithm: 
@@
 %for satisfiability by the SMT solver.
-
-%From these, we compute
-%the open automaton of an open pNet. We explain here our main
-%implementation choices.
-%:
-%\begin{itemize}
-%  \item Steps 2a-2b are merged, applying Tr2 from the
-%premisses OTs from subnets to generate OTs without
-%explicitely constructing the deduction tree.
-%  \item We define a general naming schema for implementing the fresh 
-%and clone functions with more structure than a simple global name
-%generator. It ensures unicity, but builds names
-%readable enough for debugging purpose.
-%  \item Besides that, we also have designed a management of state variables and
-%    assignments throughout the whole computation.
-%%%   \item Satisfiability check is done only at
-%%% top level of the open-transition construction. An alternative would be
-%%% to submit the satisfiability check to the SMT solver at each level of
-%%% the hierarchical OT construction, potentially reducing the overall number of
-%%% combinations. But the submission to the SMT engine is costly, and more
-%%% complexity analysis is required before deciding if this would be
-%%% worthwhile. 
-%\end{itemize}
-%
-%In the following sections, we detail:
-%\begin{itemize}
-%\item The structure of fresh variable names.
-%\item The details of the implementation for step 2a-2b, refined into:
-%  \subitem combining all possibilities of subnets activity/inactivity,
-%  \subitem matching each combination with synchronization vectors.
-%\item Management of local variables of pLTSs.
-%\item Pruning unsatisfiable OTs using the Z3 SMT solver.
-%\end{itemize}
-
-%\TODO{I have not yet been in details through the next section, but we
-%  need to shorten them...}
-
-% \TODO{Xudong: move here a (new version) of the alogorithm loplevel sketch}
-% \QIN{[Move to the head of Section 5.]}
-
-%% \QIN{
-%% The detail about the application of the Tr1 and Tr2 have not considered in the sketch, but it is an  
-%% important part in the implementation of open transition generation. 
-%% Each time we apply Tr1, there is not too much predicate terms, so do the other parameters, needed 
-%% to be generated. 
-%% When it comes to applying Tr2, the computation becomes complicated because it doing some composition of the subnets.
-%% }
-
-%\paragraph{Combining and Matching using TR2}
-%Our implementation does not build explicitly the proof trees for each
-%open transition, but instead : [Combining] enumerate all possible combinations of
-%pLTS transition (using TR1) and each synchronization vector choice
-%(TR2); [Matching] build the corresponding transition, and in particular
-%its predicate, in a hierarchical manner.
-%Each time we apply Tr2, we build a predicate as a conjunction of two
-%parts. The first part, which is the simpler one, composes the
-%predicate from the 
-%subnets and the guard from transitions in sub-pLTS or synchronization
-%vectors. The second part is the conjunction of equations generated
-%during matching the subnets' behaviors with the synchronization
-%vectors.
-
-%Note that it is simple to collect required terms in the first
-%part while in the second part we need to find out all the possible
-%conjunction forms. We present here a algorithm divided in two
-%step. Combining enumerates all the possible combinations of the
-%working status. Matching synchronizes the subnets according to
-%synchronization vectors to generate possible predicates.
-
-%Combining is to generate all the possible matchings of the subnets' OTs (open transitions). The result list of the matched tuples called *combination*.
-% 1. Initialize the result list of OT tuples.
-% 2. Get one list of OTs. It's same as get OTs of one subnet.
-% 3. Add *null* into the list, it means this subnet does not work this time.
-% 4. Combine the rest subnets' OTs. Get the combination of the rest OTs.
-% 5. If there are OTs of the chosen list not be chosen, choose one OT.
-%      1. If there are tuples of the combination not be chosen, choose one tuple.
-%          1. Add the chosen OT into the tuple.
-%          2. Add the tuple into the result list, then do the recursion.
-% 6. Return the result list.
 
@@
 
-% Mixing is to match the combination of the subnets' open transitions, hole behaviors and result action with the SV (synchronization vector) to generate the possible predicates of the OT (open transition).
-At the same time, other parameters of the OT (global state, subnets' transitions, result action...) are also generated.
-Then the possible OTs of the pNet can be achieved.
-% 1. Initialize the combination through the method *combineOpenTransitions( )*.
-% 2. Initialize the result list.
-% 3. Get the number of subnets and holes. They are used to decide how many element of the SV should be matched with them.
-% 4. For all tuples of the combination.
-%      1. Invoke the *clone( )* method to generate the fresh SV.
-%      2.
-Match the elements of the tuple with the elements of the SV.
-If there is a *null* matched with a *not null* action, filter this matching.
-Add the result expression and the predicate of the subnets into the predicate.
-Generate the target global state correspondingly.
-%      3. Match the hole behaviors with the elements of the SV. The hole behavior could be *null*. Add the result expression into the predicate.
-%      4. Match the result action with the result action of SV. Add the result expression into the predicate.
-%      5. Add the predicate into the OT. Store the OT in the result list.  
-% 5. Return the result list of all the possible OTs.
-
-%We now come to the matching using combinations from the previous step, together with hole behaviors and the result action, to match with the synchronization vectors. 
-%
-%Algorithm 2 shows the algorithm matches combination $L_C$, hole
-%behaviors $B$ with synchronization vectors $SV$. Remember variables
-%inside a synchronization vector are consider local to the vector; so every time we choose a synchronization vector $sv$ from $SV$ for matching, we clone it and use the cloned one $sv'$.
-We use the definition declared before to construct all the possible predicates but the algorithm has not checked the correctness of these predicates.
-%
-%There is one mismatch case we can easily detect here, that is its
-%working status:
-%At any time an action $e_1$ matching with an element $e_2$ from
-%synchronization vector, the pair $(e_1, e_2)$ must be checked: if both
-%$e_1$ and $e_2$ are $null$ or $not\ null$, then it continues to
-%generate a new term of predicate. Otherwise, it is intuitive that the
-%working status coming from the subnet $e_1$ is different from what
-%asked by the synchronization vector $e_2$, then this case is filtered
-%out.
-
-%\begin{algorithm}
-%\caption{Matching}
-%\begin{algorithmic}[1]
-%%\Require 
-%%The combination of subnets' open transitions $L_C$;
-%%The behaviors of the holes $B$;
-%%The set of synchronization vectors $SV$.
-%%\Ensure 
-%%The list of all the possible open transitions generated $L_{ot}$.
-%\State Initial an empty result list $L_{ot}$;
-%\For{each $C \in L_C$}
-%	\For{each $sv \in SV$}
-%		\State Clone the $sv$, the result is $sv'$;
-%		\State Generate the fresh result action $ra$;
-%		\State Combine $C, B, ra$ as a new vector $v$;
-%		\For{each $(e_1 \in v )\&\& (e_2 \in sv')$}
-%			\If{$(e_1\ is\ null\ \&\&\ e_2\ is\ not\ null)\ ||\ (e_1\ is\ not\ null\ \&\&\ e_2\ is\ null)$} 
-%			\State Skip;
-%			\Else ~ Add $(e_1 = e_2)$ into the $Pred$;
-%			\EndIf
-%		\EndFor
-%		\State Generate the result open transition $ot$ with $Pred$;
-%		\State Add the $ot$ into $L_{ot}$;
-%	\EndFor
-%\EndFor 
-%\State \Return $L_{ot}$;
-%
-%\end{algorithmic} 
-%\end{algorithm}
-
 \paragraph{Matching:} 
@@
 }
-%Algorithm 3 shows the algorithm matches
-%combination $L_C$, hole behaviors $B$ with synchronization vectors
-%$SV$ according to the definition of the predicate declared before. We
-%clone the $sv$ using the fresh function to generate a new $sv'$ with
-%fresh variables.The mismatch on working status is easy to detect so we
-%filter them in the algorithm through checking the matching elements
-%$e_1$ and $e_2$. 
-%Then we build the resulting open transition. Satisfiability of the
-%predicate is not checked at this level, but only later, at the
-%toplevel of the pNet.
 
 \paragraph{Filtering:}
-\QIN{There is already able to filter some wrong open transitions during the matching.
-We can ensure that the synchronization vector is not matched with the subnets if there is only one side not involved.
-Then we can remove the transitions from the result of matching according to the condition $\gamma$ where
-$\gamma = \bigcup_{i\in I}(v_i\in\eta\land a'_i\in\eta)\lor(v_i\in\eta\land a'_i\in\eta) .$
-}
+\TODO{Eric: 3 levels of filtering, explain our choice}
 
@@
 
-\subsection{Transition to SMTlib}
+\subsection{Translation to SMTlib}
+
+\TODO{Eric: Replace by (excerpts of) the formal version, from appendix, and reduce to less than one page}
+
+\paragraph{Presentation of algebra}
+
+As seen in section
+\ref{section:pnets}, the \emph{term algebra} used to express the
+action expressions and data parameters is left open in
+the pNet definition.
+
+So, for a given language, we now need to specify its data and action
+domains, giving them an abstract syntax (sorts, constructors, operators,
+and predicates). We call this a \emph{Presentation}.
+We also define a concrete syntax, that will be used for
+pretty-printing, but also for translating the presentation, and the
+predicates, into Z3 syntax (see the ``declare-datatypes'' statement in
+Fig~\ref{schema:smt-lib}).
+
+An algebra presentation contains:
+
+\begin{itemize}
+	\item Sorts: Constants sets of the algebra or types of the data
+          and actions (integer and boolean sort are implicitly
+          declared).  There \emph{must} be one sort for actions, and
+          eventually others for the types of data
+          parameters. In the LOTOS example, 
+          we have the $Action$ sort: $\OTvar{Action = } \{ l, \delta,
+          r, p, q, acc \} .$
+
+	\item Operators:
+          %Operators used to construct action expressions; they are
+          constructors and predicates for data and action sorts. For
+          instance, in our LOTOS example, we
+          have a generic action constructor ``$ACT$'', taking as
+          argument an action litteral and a data parameter, declared as:
+          $\OTvar{ACT:}\OTvar{< Action, Data >} \rightarrow \OTvar{Action.}$, 
+        \item Constants: The satisfiability solver need to know which
+          actions in the pLTS behaviors are constants (like the $l$, $\delta$, 
+          $r$ of the controllers in running example). 
+          For a given pNet system, the sort $Action$ will include all
+          these constants.
+\end{itemize}
+
+\paragraph{Interaction with Z3}
+%\TODO{1. example input of Z3 in SMT-LIB.[DONE] 2. software architecture.[DONE]}
+%There are several ways to interact with the Z3 solver. 
+%It is possible to use Z3 interactively using the SMT-LIB
+%(Python-based) language. 
+From inside our algorithm code, we submit satisfiability requests to
+Z3 using its JAVA API. Here for readability, we
+show the Z3 code using its SMT-LIB input language. As an
+example in
+Fig~\ref{schema:smt-lib}, we show the input for checking the
+transition of Fig.~\ref{schema:unsat-ot}. It contains the declaration
+of the LOTOS action algebra types 
+and constructors, then the declaration of variables, and finally the
+predicate to be checked, encoded as a set of assertions.
+%% Generally, some $datatypes$ are declared to input the sorts, while here
+%% we only declare one $datatypes$ named $Action$ to involve all the
+%% constant actions. Then we input the predicate of this open transition
+%% in two parts: the variables contained in the predicate are declared
+%% first, then the terms of predicate are inputed as $assertions$ one by
+%% one. 
+The result "unsat" in the output is just what we expected.
+
+%\TODO{edit the figure to make it smaller in height [DONE]}
+
+%We present the architecture of the interaction with Z3 in
+%Fig~\ref{schema:interaction}.
+%For each OT generated at the toplevel of a pNet, the predicate must be
+%submitted for satisfiability check to Z3. For that we need to
+%translate into Z3 (Java-API) syntax, both the elements of the action
+%algebra, and the predicates itself, including the encoding of the
+%variable assignments (the Post part).
+%
+%The $presentation$ of the action algebra
+%is declared at the beginning of the algorithm as the $sorts$ and the
+%$operators$ will be used throughout the whole algorithm. It is
+%translated into $datatypes$ and $functions$ then submitted to the Z3
+%at the same time. Each candidate predicate will then be translated
+%into $assertions$ before submitted to Z3 after the algorithm
+%computing out all the possible open transitions, they act as
+%intermediate results there. Together with the $datatypes$ and
+%$functions$, the $assertions$ are used to check the satisfiability of
+%the predicate in Z3.
+
+To build the input submitted to Z3 for each OT,
+we translate the algebra $presentation$, the predicates and the
+variable assignments (the Post part) into Z3 (Java-API) syntax.
+% The $presentation$ and the predicates are translated separately.
+
+\paragraph{Translation of Action algebra presentation}
+\TODO{Exerpt of the formalisation}
+The $datatypes$ are declared according to the $sorts$ the users
+declared in the $presentation$. If the return type of the $functions$
+is one of the $datatypes$, we add this $function$ to the $datatypes$ declaration.
+So when we declare the operator ACT we illustrated in section 4.1, it
+will be just declared together with the constants like :\\
+\centerline{$\OTvar{(ACT\ (action3\ Action)(data\ Int))}$}
+
+The $functions$ can also be declared independently, it usually applies to functions returning integer or boolean, in the format like:\\
+\centerline{$\OTvar{(declare\text{-}fun\ MAX\ (Int\ Int)\ Int)}$}
+
+%Although in Fig~\ref{schema:smt-lib} we have not declared $functions$ outside of $datatypes$, there still exists $functions$ declared independently.
+The input and output types of the $function$ are also determined by the construct of the  $operators$ in the presentation.
+For example, we define a new operator to present the equation between two actions in LOTOS example $\text{EQUAL}$ in the format likes:
+%
+%\[EQUAL: \quad < Action , Action > \rightarrow Bool .\]
+%
+%It will be translated into the Z3 statement: 
+%
+%\[\text{(declare-fun\ EQUAL\ (Action\ Action)\ Bool) .}\]
+
+\paragraph{Translating assignments into predicate terms}
+\TODO{Exerpt of the formalisation}
+
+%The assignments are also taken into account when checking the
+%satisfiability of the open transitions as they represent the value of
+%the variables involved in an OT. In order to do that, we employs a
+%translation from assignments into term of predicates. The assignments
+%required to be translated are only those belong to the variables
+%contain in the start states of the open transitions. The assignments
+%are represented as equations between the variables and the expressions
+%on the right side of assignment. For the assignments of the same
+%variable, we do not figure out which state is the precursor of current
+%state, we keep all these possible equations instead, and generate the
+%disjunction of these equations. The state could always move to the
+%target state if there exists one of the values of its variable
+%satisfies the guard.
+%%\TODO{It won't matter the variable of the next state
+%%except that the right hand side expression contain its variables. This
+%%is a problem left to be solved in our future work. WHICH PROBLEM ?}
+%After that, for the assignments of the different variables, we generate a conjunction of them. This way we obtain a new term of the predicate involving assignments of the variables.
+
+State-variable assignments are also treated as a part of the
+predicates when checking the satisfiability. % Here we need conduct some
+% translations,
+For each assignement in a $\Post$ predicate, such as $\{s_0 \leftarrow 1\}$ in section
+~\ref{section:op-semantics}, we translate it into an equation
+$s_0=1$. For several assignments of the same variable in the same state,
+we generate the disjunction of 
+these equations. Correspondingly, we generate a conjunction for the
+assignments from different variables.
+
+\paragraph{Checking satisfiability}
+
+% We check the satisfiability of open transitions on the top level of
+% the pNet, treating these open transitions as the intermediate result
+% of the algorithm. After we get the intermediate results of open
+% transitions, we check them one by one.
+Here we declare first all the variables in the predicates, with their
+sorts.
+An example of syntax is::\\
+\centerline{$\OTvar{(declare-const\ |:ra:1:1|\ Action)}$}
+
+\noindent Then each term of the
+predicate is an assertion in Z3, as an example, in the former
+unsatisfiable result in Fig~\ref{schema:unsat-ot}, the contradiction is occurred in terms: \\
+\centerline{$\OTvar{(:ra:11:1=l)} \OTland \OTvar{(delta=:ra:11:1)}$}\\
+from which we generate the following two assertions:\\
+\centerline{$\OTvar{(assert\ (=\ |:ra:11:1|\ l))\ \ \ (assert\ (=\ delta\ |:ra:11:1|))}$}
+
+\noindent The predicate submitted to the Z3 also contains the
+assignments encodings.
+In the case of $ot_2$, it
+gives the assertion:\\
+\centerline{$\OTvar{assert (or (= var\_s0 0) (= var\_s0 01)))}$}
+
+\subsection{Simplification of Predicates}
+\ERIC{: motivated, add refs, and an abstract presentation of stuff from pages 19-20}
+
+\subsection{Result of the running example}
+\label{section:full-result}
+
+\TODO{Xudong: Update: we have 11 satisfiable OTs here}
+Our tool builds 30 open
+transitions, out of which 27 are detected unsatisfiable by Z3, we
+get only 3 results left; the resulting open automaton is shown in
+Fig. ~\ref{schema:lotos-result}, together with its open transitions.
+
+The resulting open transitions represent all the
+possible movements of the LOTOS example.
+What can be observed is any actions of the process $P$ from the beginning, until $P$ performs a $\delta(x)$ and the value of
+$x$ is transmitted to the $acc(x);Q$ giving out a silent action. Such behavior is performed by the $ot_1$ then $ot_2$. 
+Then it keeps presenting the behavior of $Q$, as seen in $ot_3$. 
+%The $ot_1$ transition means that the actions of the process $P$ could
+%be transmitted out, until $P$ performs a $\delta(x)$ and the value of
+%$x$ is transmitted, through transition
+%$ot_2$. The other 3 open transitions shows the behaviors of the
+%process $Q$ while the $ot_3$ and $ot_4$ won't be performed as the
+%controller has already set the value $s_0$ to 1 in the previous
+%action.
+
+\begin{figure}[t]
+   \centerline{\includegraphics[width=12cm]{XFIG/BIPresult-ArchFailureTimerMax}}
+   \caption{Open Automaton\TODO{syntax could be better...}}  \label{schema:resultOA}
+ \end{figure}
+
+\begin{figure}[h]
+%  \centerline{\includegraphics[width=5cm]{XFIG/LOTOSresult}}
+  \TODO{Detaisl of some OTs of the FailureTimer}
+
+$\begin{array}{@{}r@{}l@{}}
+    ot_1  = &\openrule{\{0 \xrightarrow{l}_{C_1} 0\}, ~~\{\xrightarrow{hb_{1}}_P\}, ~~[s_0=0 \!\land\! hb_{1} \neq \delta(x) \!\land\! v_1=hb_{1}]}
+    {\ostate{00} \xrightarrow{v_1} \ostate{00}}\\
+  \end{array}$
+
+$\begin{array}{@{}r@{}l@{}}
+    ot_2  = &\openrule{\{0 \xrightarrow{\delta}_{C_1} 0, 0 \xrightarrow{acc(x)}_{C_2} 1\}, ~~\{\xrightarrow{hb_{2}}_P\}, ~~[s_0=0 \!\land\!
+hb_{2}=\delta(x) \!\land\!
+v_2=\underline{\delta(x)}], ~~\{s_0 \xleftarrow{} 1\}}
+    {\ostate{00} \xrightarrow{v_2} \ostate{01}}\\
+  \end{array}$
+
+\caption{The open automaton of the LOTOS formula}  \label{schema:lotos-result}
+\end{figure}
+
+%\subsubsection{Result of CCS example}
+%\QIN{
+%also can present all the possible behavior of that CCS formula with 16 open
+%transitions in Fig. ~\ref{schema:ccs-result}, here we omitted the details of open transitions. 
+%In this example, there are 32 more transitions detected unsatisfiable by Z3.
+%}
+%
+%\QIN{
+%Here we only show one of the result transitions. It presents the value-passing between $a.P$ and $b.Q$ and they are synchronized then
+%give out an silent action $\tau$, process $P$ and $Q$ should not work in this case.
+%}
+%
+%\begin{figure}[h]
+%  \centerline{\includegraphics[width=5cm]{XFIG/CCSresult}}
+%  
+%  $\begin{array}{@{}r@{}l@{}}
+%    ot_1  = &\openrule{\{0 \xrightarrow{a}_{C_1} 1, 0 \xrightarrow{b}_{C_2} 1\}, ~~a=!ch_{11}(v_{11}) \!\land\! b=?ch_{11}(v_{11}) \!\land\! a\neq l \!\land\! b\neq r\!\land\! v_1=\tau}
+%    {\ostate{00} \xrightarrow{v_1} \ostate{11}}\\
+%  \end{array}$
+%  
+%\caption{The open automaton of the CCS parallel formula}  \label{schema:ccs-result}
+%\end{figure}
+
+%% \QIN{
+%% To sum up, from the pNets encoding the formulas of given algebra, which inputed by the user, we can exactly construct
+%% the open automaton for them. 
+%% }
+
+\section{Conclusion and Discussion}
+\label{section:conclusion}
+
+In this paper we presented the algorithm for generating an open
+automaton representing the semantics of an open pNet, and we described
+the implementation of the
+algorithm. Our implementation includes two main parts. First, we
+compute all the possible open transitions. The actions in pLTS and
+hole behaviors are composed in the algorithm while the generation of
+predicate need to match the combinations of the subnets with the
+synchronization vectors. Some of the open transitions obtained at this
+intermediate step, constructed in a structural manner from all
+possible combinations of possible logical predicates, may
+contain predicates which do not represent any possible concrete
+instantiations. 
+To get rid of these useless transitions, we use the SMT solver Z3 for checking the
+satisfiability of the predicate in each open transition. In
+order to do that, we encode into Z3 the action algebra presentation,
+the a representation of the predicates, before submitting them to the
+Z3 solver. We implemented our algorithm in the VerCors platform and use some
+running examples, encoding expressions from various process algebras, to test the
+algorithm. Our use-cases show that our encoding
+identifies successfully all unsatisfiable open transitions and that
+the resulting automaton reflects correctly the expected 
+movements of the encoded process expressions.
+
+Among the questions arising during this work, an important one is the
+efficiency of Z3 for our needs. Z3 is famous for being very fast for
+solving very large sets of assertions, and this could be important for
+us. But we encountered  some problems during the implementation the
+checking method using Z3. For example, if the $functions$ and the
+$datatypes$ part of the algebra presentation we submit to the solver
+are independent with each other, then checking the $assertions$ is a
+simple work. However, $functions$ on recursive $datatypes$ make it
+more complex, some special rules might be defined by user for the
+induction. Also, we need more evidence that dealing with more complex
+action algebras, that would involve axiomatizing their data structures
+into Z3 theories, will indeed allow us to decide validity of
+predicates.
+We may also try other automatic theorem provers, depending on the structure of the proofs we need.
+
+\TODO{Change perspective: we are working on the formal extensino of
+  BIB architectures, and their semantics in terms of pNets. Then
+  bisimulation and model-checking principles adapted to open pNet
+  systems are under development}
+
+Naturally, our next goals after the generation of the open automata
+will be to model-check, and to check equivalence of  pNets. While
+model-checking open automata (with a suitable logic including
+predicates on data) seems easy to define, equivalence checking is more challenging.
+In previous paper, we
+have already found the FH-bisimulation, inspired by~\cite{deSimone85} as a
+suitable definition. But usual approaches of bisimulation by partition
+refinement does not work easily with symbolic transitions. In a first
+step we may want instead to define and implement an algorithm for
+checking that a given equivalence relation between open automata 
+states is indeed a FH-Bisimulation. Finding automatically a
+bisimulation relation or the most general bisimulation will be more
+challenging. It appears also that when comparing different pNets with
+different structure, strong bisimulation will be too strong a notion,
+and that we will have to define proper notions of weak equivalence or
+refinements.
+
+Before that work, we need to reconsider the result open transitions
+from our algorithm. The ideal
+result that we showed in the bottom part of
+Fig.~\ref{schema:lotos-result} is not the one generated by the algorithm,
+because the original one contains many intermediate
+variables, such as fresh local variables of synchronization
+vectors, and fresh result variables of intermediate open transitions.
+Such intermediate variables come from the way predicates are
+generated, and depends on the particular structure of the pNet. But
+they are not significant in the resulting behavior, and should be
+eliminated before comparing such behavior with another pNet.
+To eliminate the intermediate variables in the predicate, we want to define
+the set of the significant variables that we won't eliminate: the
+local variables of pLTS transitions, the hole behaviors and the result
+action at the top level.
+The result of the elimination will be simpler predicates, that can be
+successfully compared (e.g. by Z3) within the bisimulation checking
+algorithm.
+
+\bibliographystyle{lncs/splncs}
+
+% \bibliography{oasis,biblio}
+\bibliography{biblio}
+
+% \newpage
+\appendix
+
+\section{More details on the generation algorithm}
+\subsection{Algebra specification}
+\subsection{Term algebra: type system and static semantics}
+Our models rely on a notion of parameterized actions, that are
+symbolic expressions using data types and variables. As our model aims
+at encoding the low-level behavior of possibly very different
+programming languages, we do not want to impose one specific algebra
+for denoting actions, nor any specific communication mechanism. So we
+leave unspecified the constructors of the algebra that will allow building
+expressions and actions. Moreover, we use a generic {\em action interaction}
+mechanism, based on unification between two or more action
+expressions. This will be used in the semantics of synchronization
+vectors to express various kinds of communication or synchronization mechanisms.
+
+\def\Talg{\mathcal{T}_{\Sigma,\P}}
+Formally, we assume the existence of a term algebra $\Talg$,
+where $\Sigma$ is the signature of the data and action constructors,
+and $\P$ a set of variables. Within $\Talg$, we distinguish a set of
+data expressions $\mathcal{E}_\P$, including a set of boolean
+expressions $\mathcal{B}_{\P}$ ($\mathcal{B}_{\P}\subseteq\mathcal{E}_\P$).
+On top of $\mathcal{E}_\P$ we build the action algebra
+$\mathcal{A}_\P$, with $\mathcal{A}_P\subseteq\mathcal{T}_\P,
+\mathcal{E}_P\cap\mathcal{A}_P=\emptyset$;
+naturally action terms will use data expressions as sub-terms.
+The function $\vars(t)$ identifies the set of variables in a term
+$t\in\AlgT$.
+
+pNets can encode naturally the notion of input actions as found e.g. in value-passing CCS
+\cite{Milner89} or of usual point-to-point message passing calculi, but it also allows
+for more general mechanisms, like gate negotiation in Lotos, or broadcast
+communications.
+
+\subsection{Fresh variables}
+
+%The variables in each synchronization vector are considered local, so
+%does the variables of an open transition such as its hole behaviors
+%and its result action. So we want rename the variables to make them
+%unique on every occurrence of a vector. Similarly, the name given to
+%the hole behaviors for each hole or the result action for each open
+%transition must be distinct. At the same time, we also hope them still
+%readable. Here we rename the variables with a regular format using the fresh function.
+
+Application of the semantic rules require generating a lot of fresh
+names, for different kind of variables. We could use a global name
+generator to guarantee unicity, but 
+at the same time, we also hope them still
+readable. Here we rename the variables with a regular format using the fresh function.
+More precisely, the fresh function generates a new name adding a
+suffix after the original name. The suffix contains three parts
+combined by a colon.
+
+\begin{definition}[Fresh variable]\label{fresh-variable}
+The format of \emph{fresh variable} (renaming) is defined as:
+``$\emph{prefix : tree\ index\ :\ counter}$''.
+\begin{itemize}
+   \item[$\bullet$] $prefix$ identifies the kind of the
+     variable. current kinds are: sva (SV action), ra (result action), hb (hole behavior).
+   \item[$\bullet$] $tree\ index$ is the index of the node containing the variable in the tree-like structure of the pNet.
+   \item[$\bullet$] $counter$ is the current value of the corresponding counter.
+\end{itemize}
+\end{definition}
+
+%\TODO{Option: Add the process and the vector ids ?}
+
+%$Prefix$ avoids the confusion between variables from different structures with the same name by attaching the type of the structure.
+$Tree\ index$ is given to every node of the pNets to mention which node the variable belongs to as pNets has a tree-like structure.
+To each node, the tree index is always a number sequence of the tree index of its higher level and the index of the node in this level at the last.
+$A\ set\ of\ counters$ is used to count the current times the SV, Hole, subnet invoked, or the number of possible OT generated to provide an identity.
+
+For example, in the running example, the first possible behavior of
+the hole, it doesn't have a name, only have the prefix ``hb''. The
+hole is the second subnets of the root node so its ``tree index'' is
+``12''. The fresh variable name is ``$\OTvar{:hb:12:1}$''. 
+\subsection{Variable managment}
+The variables in each synchronisation vector are considered local: for a given pNet expression, we must have fresh local variables for each occurrence of a vector (= each time we instantiate rule Tr2).
+Similarly the state variables of each copy of a given pLTS in the system, must be distinct, and those created for each application of Tr2 have to be fresh and all distinct.
+This will be implemented within the open-automaton generation algorithm, e.g.
+using name generation using a global counter as a suffix.
+\subsection{Filtering the behaviour combinations}
+\QIN{There is already able to filter some wrong open transitions during the matching.
+We can ensure that the synchronization vector is not matched with the subnets if there is only one side not involved.
+Then we can remove the transitions from the result of matching according to the condition $\gamma$ where
+$\gamma = \bigcup_{i\in I}(v_i\in\eta\land a'_i\in\eta)\lor(v_i\in\eta\land a'_i\in\eta) .$
+}
+\subsection{Translation to SMTlib input language}
 In order to submit satisfiability problems to Z3 (for the predicates
@@
 
-\TODO{[DONE][Xudong]: Give an example of defining $Tau$ and $Emit$ using the (new
-  version of) the API}
-
-\subsubsection{Expressions}
+\paragraph{Expressions}
 Once an algebra presentation is defined, we can construct expressions
@@
 expressions respect the arity of operators), and typing rules.
+\TODO{Eric: refer in the appendix header}
 
@@
 \smallskip
-\ERIC{My plan here is to provide the translation principles as some
-  high-level pseudo code, together with precise definition of the
-  translation functions of a presentation+environment, and of a
-  predicate (including expressions)}
+%% \ERIC{My plan here is to provide the translation principles as some
+%%   high-level pseudo code, together with precise definition of the
+%%   translation functions of a presentation+environment, and of a
+%%   predicate (including expressions)}
 
@@
 
-\subsubsection{Presentation Translation}
+\subsubsection{Presentation Translation} \TODO{Duplicate ?}
 We define here the translation of the algebra presentation, extended
@@
 \end{definition}
-
-\TODO{[Xudong: this is certainly obsolete?] At the same time, we have
-  several internal lists (actually hash 
-  maps) \texttt{exprs}, \texttt{funcDecls}, \texttt{sortDatatypes} to
-  store the generated Z3 objects with their names for later proofs.}
 
@@
 \noindent
+\TODO{This is incomplete... Xudong: Conjunctive normal form, translation function for boolean expressions, + assignments}
+
 \begin{tabular}{p{5cm}p{5cm}p{2.5cm}}
@@
 \TODO{[Eric]: Motivate, and refs  -- reduce the section here to approx
-  half a page} 
+  half a page (from the next two pages...)}
+
+\subsection{Elimination of intermediate variables}
+
 \QIN{
@@
 
-\subsection{Result of the running example}
-\label{section:full-result}
-
-\TODO{Update: we have 11 satisfiable OTs here}
-Our tool builds 30 open
-transitions, out of which 27 are detected unsatisfiable by Z3, we
-get only 3 results left; the resulting open automaton is shown in
-Fig. ~\ref{schema:lotos-result}, together with its open transitions.
-
-The resulting open transitions represent all the
-possible movements of the LOTOS example.
-What can be observed is any actions of the process $P$ from the beginning, until $P$ performs a $\delta(x)$ and the value of
-$x$ is transmitted to the $acc(x);Q$ giving out a silent action. Such behavior is performed by the $ot_1$ then $ot_2$. 
-Then it keeps presenting the behavior of $Q$, as seen in $ot_3$. 
-%The $ot_1$ transition means that the actions of the process $P$ could
-%be transmitted out, until $P$ performs a $\delta(x)$ and the value of
-%$x$ is transmitted, through transition
-%$ot_2$. The other 3 open transitions shows the behaviors of the
-%process $Q$ while the $ot_3$ and $ot_4$ won't be performed as the
-%controller has already set the value $s_0$ to 1 in the previous
-%action.
-
-\begin{figure}[t]
-   \centerline{\includegraphics[width=12cm]{XFIG/BIPresult-ArchFailureTimerMax}}
-   \caption{Open Automaton\TODO{syntax could be better...}}  \label{schema:resultOA}
- \end{figure}
-
-\begin{figure}[h]
-%  \centerline{\includegraphics[width=5cm]{XFIG/LOTOSresult}}
-  \TODO{Detaisl of some OTs of the FailureTimer}
-
-$\begin{array}{@{}r@{}l@{}}
-    ot_1  = &\openrule{\{0 \xrightarrow{l}_{C_1} 0\}, ~~\{\xrightarrow{hb_{1}}_P\}, ~~[s_0=0 \!\land\! hb_{1} \neq \delta(x) \!\land\! v_1=hb_{1}]}
-    {\ostate{00} \xrightarrow{v_1} \ostate{00}}\\
-  \end{array}$
-
-$\begin{array}{@{}r@{}l@{}}
-    ot_2  = &\openrule{\{0 \xrightarrow{\delta}_{C_1} 0, 0 \xrightarrow{acc(x)}_{C_2} 1\}, ~~\{\xrightarrow{hb_{2}}_P\}, ~~[s_0=0 \!\land\!
-hb_{2}=\delta(x) \!\land\!
-v_2=\underline{\delta(x)}], ~~\{s_0 \xleftarrow{} 1\}}
-    {\ostate{00} \xrightarrow{v_2} \ostate{01}}\\
-  \end{array}$
-
-\caption{The open automaton of the LOTOS formula}  \label{schema:lotos-result}
-\end{figure}
-
 %\subsubsection{Result of CCS example}
@@
 %% }
-
-\section{Conclusion and Discussion}
-\label{section:conclusion}
-
-In this paper we presented the algorithm for generating an open
-automaton representing the semantics of an open pNet, and we described
-the implementation of the
-algorithm. Our implementation includes two main parts. First, we
-compute all the possible open transitions. The actions in pLTS and
-hole behaviors are composed in the algorithm while the generation of
-predicate need to match the combinations of the subnets with the
-synchronization vectors. Some of the open transitions obtained at this
-intermediate step, constructed in a structural manner from all
-possible combinations of possible logical predicates, may
-contain predicates which do not represent any possible concrete
-instantiations. 
-To get rid of these useless transitions, we use the SMT solver Z3 for checking the
-satisfiability of the predicate in each open transition. In
-order to do that, we encode into Z3 the action algebra presentation,
-the a representation of the predicates, before submitting them to the
-Z3 solver. We implemented our algorithm in the VerCors platform and use some
-running examples, encoding expressions from various process algebras, to test the
-algorithm. Our use-cases show that our encoding
-identifies successfully all unsatisfiable open transitions and that
-the resulting automaton reflects correctly the expected 
-movements of the encoded process expressions.
-
-Among the questions arising during this work, an important one is the
-efficiency of Z3 for our needs. Z3 is famous for being very fast for
-solving very large sets of assertions, and this could be important for
-us. But we encountered  some problems during the implementation the
-checking method using Z3. For example, if the $functions$ and the
-$datatypes$ part of the algebra presentation we submit to the solver
-are independent with each other, then checking the $assertions$ is a
-simple work. However, $functions$ on recursive $datatypes$ make it
-more complex, some special rules might be defined by user for the
-induction. Also, we need more evidence that dealing with more complex
-action algebras, that would involve axiomatizing their data structures
-into Z3 theories, will indeed allow us to decide validity of
-predicates.
-We may also try other automatic theorem provers, depending on the structure of the proofs we need.
-
-\TODO{Change perspective: we are working on the formal extensino of
-  BIB architectures, and their semantics in terms of pNets. Then
-  bisimulation and model-checking principles adapted to open pNet
-  systems are under development}
-
-Naturally, our next goals after the generation of the open automata
-will be to model-check, and to check equivalence of  pNets. While
-model-checking open automata (with a suitable logic including
-predicates on data) seems easy to define, equivalence checking is more challenging.
-In previous paper, we
-have already found the FH-bisimulation, inspired by~\cite{deSimone85} as a
-suitable definition. But usual approaches of bisimulation by partition
-refinement does not work easily with symbolic transitions. In a first
-step we may want instead to define and implement an algorithm for
-checking that a given equivalence relation between open automata 
-states is indeed a FH-Bisimulation. Finding automatically a
-bisimulation relation or the most general bisimulation will be more
-challenging. It appears also that when comparing different pNets with
-different structure, strong bisimulation will be too strong a notion,
-and that we will have to define proper notions of weak equivalence or
-refinements.
-
-Before that work, we need to reconsider the result open transitions
-from our algorithm. The ideal
-result that we showed in the bottom part of
-Fig.~\ref{schema:lotos-result} is not the one generated by the algorithm,
-because the original one contains many intermediate
-variables, such as fresh local variables of synchronization
-vectors, and fresh result variables of intermediate open transitions.
-Such intermediate variables come from the way predicates are
-generated, and depends on the particular structure of the pNet. But
-they are not significant in the resulting behavior, and should be
-eliminated before comparing such behavior with another pNet.
-To eliminate the intermediate variables in the predicate, we want to define
-the set of the significant variables that we won't eliminate: the
-local variables of pLTS transitions, the hole behaviors and the result
-action at the top level.
-The result of the elimination will be simpler predicates, that can be
-successfully compared (e.g. by Z3) within the bisimulation checking
-algorithm.
 

### 2018-01-15 2017-Xudong-SMT/FM-2018-extended.tex
dessin et listing

@@
 \usepackage[T1]{fontenc}
-\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
-\geometry{a4paper}                   % ... or a4paper or a5paper or ...
+% \usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
+%\geometry{a4paper}                   % ... or a4paper or a5paper or ...
 %\geometry{landscape}                % Activate for for rotated page geometry
@@
 extended with explicite data in synchronisations, and we compute their
-open automaton semantics. Cet automate peut alors être utilisé pour
-monter les propriétés comme, \TODO{ par exemple ..}
+open automaton semantics. This automaton may then be used to prove
+bahavioral properties, like e.g., \TODO{ par exemple ..}
 
@@
 
+ %% \begin{figure}[t]
+ %%   \centerline{\includegraphics[width=12cm]{XFIG/BIPspec-ArchFailureTimerMax}}
+ %%   \caption{FailureTimer Architecture in BIP graphical syntax}  \label{schema:BIParchitecture}
+ %% \end{figure}
+
 \begin{figure}[t]
-   \centerline{\includegraphics[width=12cm]{XFIG/BIPspec-ArchFailureTimerMax}}
-   \caption{FailureTimer Architecture in BIP graphical syntax}  \label{schema:BIParchitecture}
- \end{figure}
-
-\begin{figure}[t]
-   \centerline{\includegraphics[width=12cm]{XFIG/BIPpnet-ArchFailureTimerMax}}
+   \centerline{\includegraphics[width=12cm]{XFIG/FailureTimerPNET}}
    \caption{FailureTimer pNet encoding}  \label{schema:BIParchitecture}
@@
 \subsection{Full output for the FailureTimer open automaton}
+
+\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, frame=single]
+    {s0---failure(true)-->s1, t0---start(true)-->t1}, {---:hb_B:13:1-->},
+    (failure(true)=failure(b1:sva_SV0:1:1))/\(start(true)=start(b2:sva_SV0:1:1))
+    /\(:hb_B:13:1=fail(b0:sva_SV0:1:1))/\((b1:sva_SV0:1:1=b2:sva_SV0:1:1)
+    /\(~(b1:sva_SV0:1:1\/b2:sva_SV0:1:1)\/b0:sva_SV0:1:1))/\(_fail_=:ra:1:1),   {t := 4}
+OT ------------------------------------------------------------
+        <s0_t0>-----:ra:1:1----><s1_t1>
+
+        {s0---resume(false)-->s0, t0---resume(false)-->t0},   {---:hb_B:16:2-->},
+        (resume(false)=resume(b1:sva_SV1:1:2))/\(resume(false)=resume(b2:sva_SV1:1:2))
+        /\(:hb_B:16:2=resume(b0:sva_SV1:1:2))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2)
+        /\(~(b1:sva_SV1:1:2\/b2:sva_SV1:1:2)\/b0:sva_SV1:1:2))/\(_resume_=:ra:1:2),   {}
+OT ------------------------------------------------------------
+        <s0_t0>-----:ra:1:2----><s0_t0>
+
+    {},   {---:hb_B:118:6-->},   (:hb_B:118:6=finish)/\(finish=:ra:1:6),   {}
+OT ------------------------------------------------------------
+        <s0_t0>-----:ra:1:6----><s0_t0>
+
+        {s1---failure(false)-->s1, t1---start(false)-->t1},   {---:hb_B:13:1-->},
+        (failure(false)=failure(b1:sva_SV0:1:1))/\(start(false)=start(b2:sva_SV0:1:1))
+        /\(:hb_B:13:1=fail(b0:sva_SV0:1:1))/\((b1:sva_SV0:1:1=b2:sva_SV0:1:1)
+        /\(~(b1:sva_SV0:1:1\/b2:sva_SV0:1:1)\/b0:sva_SV0:1:1))/\(_fail_=:ra:1:1),   {}
+OT ------------------------------------------------------------
+        <s1_t1>-----:ra:1:1----><s1_t1>
+
+        {s1---resume(true)-->s0, t1---resume(true)-->t0},   {---:hb_B:16:2-->},
+        (resume(true)=resume(b1:sva_SV1:1:2))/\(resume(true)=resume(b2:sva_SV1:1:2))
+        /\(:hb_B:16:2=resume(b0:sva_SV1:1:2))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2)
+        /\(~(b1:sva_SV1:1:2\/b2:sva_SV1:1:2)\/b0:sva_SV1:1:2))/\(_resume_=:ra:1:2),   {}
+    OT ------------------------------------------------------------
+        <s1_t1>-----:ra:1:2----><s0_t0>
+
+        {t1---tick-->t1},   {},   (t!=0)/\(_tick_=:ra:1:3),   {t := (t-1)}
+    OT ------------------------------------------------------------
+        <s1_t1>-----:ra:1:3----><s1_t1>
+
+        {},   {---:hb_B:118:6-->},   (:hb_B:118:6=finish)/\(finish=:ra:1:6),   {}
+    OT ------------------------------------------------------------
+        <s1_t1>-----:ra:1:6----><s1_t1>
+
+        {s1---timeout-->s2, t1---timeout-->t0},   {},   (t=0)/\(ask=:ra:1:4),   {}
+    OT ------------------------------------------------------------
+        <s1_t1>-----:ra:1:4----><s2_t0>
+
+        {s2---resume(false)-->s2, t0---resume(false)-->t0},   {---:hb_B:16:2-->},
+        (resume(false)=resume(b1:sva_SV1:1:2))/\(resume(false)=resume(b2:sva_SV1:1:2))
+        /\(:hb_B:16:2=resume(b0:sva_SV1:1:2))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2)
+        /\(~(b1:sva_SV1:1:2\/b2:sva_SV1:1:2)\/b0:sva_SV1:1:2))/\(_resume_=:ra:1:2),   {}
+    OT ------------------------------------------------------------
+        <s2_t0>-----:ra:1:2----><s2_t0>
+
+        {s2---reset-->s0},   {},   (reset=:ra:1:5),   {}
+    OT ----------------------------------------------------------
+        <s2_t0>-----:ra:1:5----><s0_t0>
+
+        {},   {---:hb_B:118:6-->},   (:hb_B:118:6=finish)/\(finish=:ra:1:6),   {}
+    OT ------------------------------------------------------------
+        <s2_t0>-----:ra:1:6----><s2_t0>
+\end{lstlisting}
+
 \subsection{Scaling up: several subsystems on the same bus}

### 2018-01-15 2017-Xudong-SMT/FM-2018-extended.tex
dessins corriges
Update example of Z3 input.
Fig.[unsat-ot] and Fig.[smt-lib] in section "Pruning the unsatisfiable results".

@@
 %{s0---delta-->s0},   {---:hb_P:12:1-->},   (:ra:11:1=l)/\(delta=:ra:11:1)/\(var_s0=0)/\(:hb_P:12:1=a1:sva_SV0:1:1)/\(:ra:1:1=a1:sva_SV0:1:1)/\(a1:sva_SV0:1:1!=delta(x)),   {var_s0 := 1}
-$\begin{array}{@{}r@{}l@{}}
-    ot  = &\openrule{\{0 \xrightarrow{\delta} 0\}, ~~\{\xrightarrow{:hb:12:1}\}, ~~\OTvar{:ra:11:1}=l \OTland \delta=\OTvar{:ra:11:1} \OTland \OTvar{s0}=0 \\
-     \OTland \OTvar{:hb:12:1}=\OTvar{a1:sva:1:1} \OTland \OTvar{:ra:1:1}=\OTvar{a1:sva:1:1} \OTland \OTvar{a1:sva:1:1} \neq \delta(x), ~~\{\OTvar{s0} \leftarrow 1\}}
-    {\ostate{00} \xrightarrow{\OTvar{:ra:1:1}} \ostate{00}}\\
+$\begin{array}{r@{}l}
+    ot  = &\openrule{\{0 \xrightarrow{\OTvar{resume(false)}} 0, 0 \xrightarrow{\OTvar{start(true)}} 1\}, ~~\{\xrightarrow{hb}\},~~\OTvar{resume(false)}=\OTvar{failure(}\OTvar{b}_1\OTvar{)}\\
+    			     \OTland \OTvar{start(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)} \OTland \OTvar{hb}=\OTvar{fail(}\OTvar{b}_0\OTvar{)} \OTland \OTvar{v}=\OTvar{\underline{fail}}\\
+			     \OTland \OTvar{b}_1 = \OTvar{b}_2 \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
+    	   {\ostate{00} \xrightarrow{\OTvar{v}} \ostate{01}}\\
   \end{array}$
-\caption{One of the unsatisfiable open transitions in LOTOS running example}  \label{schema:unsat-ot}
+\caption{One of the unsatisfiable open transitions in FailureTimer}  \label{schema:unsat-ot}
 \end{figure}
@@
   %  \centerline{\includegraphics[width=12cm]{XFIG/SMTLIB2}}
-    \centerline{\includegraphics[width=\linewidth]{XFIG/SMTLIB2}}
+    \centerline{\includegraphics[width=\linewidth]{XFIG/SMTLIB3}}
   \caption{The input of the Z3 solver in SMT-LIB language and the output result}  \label{schema:smt-lib}
@@
    /\(:hb_B:13:1=fail(b0:sva_SV0:1:1))/\((b1:sva_SV0:1:1=b2:sva_SV0:1:1)
-    /\(~(b1:sva_SV0:1:1\/b2:sva_SV0:1:1)\/b0:sva_SV0:1:1))/\(_fail_=:ra:1:1),   {t := 4}
+   /\(~(b1:sva_SV0:1:1\/b2:sva_SV0:1:1)\/b0:sva_SV0:1:1))/\(_fail_=:ra:1:1),
+   {t := 4}
 OT ------------------------------------------------------------
@@
    /\(:hb_B:16:2=resume(b0:sva_SV1:1:2))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2)
-        /\(~(b1:sva_SV1:1:2\/b2:sva_SV1:1:2)\/b0:sva_SV1:1:2))/\(_resume_=:ra:1:2),   {}
+   /\(~(b1:sva_SV1:1:2\/b2:sva_SV1:1:2)\/b0:sva_SV1:1:2))/\(_resume_=:ra:1:2),
+   {}
 OT ------------------------------------------------------------

### 2018-01-15 2017-Xudong-SMT/FM-2018-extended.tex
algo

--- 2018-01-15 2017-Xudong-SMT/FM-2018-extended.tex
@@
 \label{section:implementation}
-
-\TODO{Eric: add a header, reorganise the parts of the algorithm}
-
 In this section we describe the algorithm implementing the pNet
@@
 
-\TODO{Eric: rewrite}
-We have already have the sketch of computing the open automata \cite{???}.
-While in our implementation we does not build explicitly a proof tree for every open transition.
-Instead, we repeat applying the Tr1 or Tr2 to generate the sub-transitions.
-Tr1 is applied on the leaf (pLTS) simply take the pLTS transitions through the given start state and add the predicate in pNet to generate the open transition.
-When applying Tr2 we use two methods, combining and matching, to generate the new predicate of the open transitions in a hierarchical manner
-as in this case the composition the subnets brings more constraints for synchronizing behaviors. 
-Beside the new generated predicate, the predicates from the subnets are also added as a conjunction with those new predicates.
+Our algorithm starts with an open pNet, and builds its set of open
+transitions (OTs). Its main loop is a classical residual algorithm: starting
+from the initial global state, it pick a state in an unexplored set, and
+computes all possible OTs, adding their target states in the
+unexplored set, until this set is empty. As the potential set of
+global states is finite (see \cite{henrio:Forte2016}), this terminates.
+
+The inside loop (\emph{MakeTransitions} method) applies recursively
+the semantic rules following the structure of the pNet. 
+For pLTS at leaves, rule Tr1 simply take the pLTS transitions of the
+corresponding local state and build the predicate to generate the
+open transition. 
+On a pNet node to apply rule Tr2 we use two methods, combining and
+matching, to generate the new predicate of the open transitions in a
+hierarchical manner.
+
+Last, at the root of the pNet, the predicate of each OT is translated
+into SMTlib assertions, and checked for satifiability. Unsatisfiable
+OTs are pruned, and the final open automaton is computed as the set of
+global states reachable by satisfiable OTs.
 
@@
 
-%Algorithm 1 shows the main structure of the algorithm: 
-%the computation repeats applying Tr1 and Tr2 to build all possible
-%combinations of behaviors of pLTS and Holes, through all possible
-%synchronisation vectors. The resulting open transitions are checked
-%for satisfiability by the SMT solver.
-
-%We first conduct combining. For each subnet, we enumerate all the
-%possible cases of its working status. The result action of a pLTS or a
-%pNet is the external action of the node shows the working status of
-%it.
 %
@@
 %
-%Algorithm 1 shows the combining algorithm for enumerating all the possible combinations of open transitions.
-The algorithm initializes an empty list $L_C$.
-Dealing with the list $TR$ containing several sets of open transitions from different subnets, the algorithm only chooses one of sets $L_{ot}$ and does combining on the remaining part of $TR$ recursively then get a partial result of combining, $L'_C$.
-Since there could exist the case that the subnet is not working, a $null$ is added into the $L_{ot}$ to represent it.
-We get much more combinations after combining $ot$ from $L_{ot}$ with the partial result.
-
-%\begin{algorithm}
-%\caption{Combining}
-%\begin{algorithmic}[1]
-%
-%%\Require The list $TR$ of the open transition sets of the subnets. 
-%%\Ensure The list of all the possible combinations of open transitions $L_C$.
-%\State Initialize an empty combination list $L_C$;
-%\State Extract a list of open transitions $L_{ot}$ from $TR$;
-%\State Add $null$ to $L_{ot}$;
-%\State Get the combinations $L'_C$ of the $TR$;
-%\For{each $ot \in L_{ot}$}
-%	\For{each $C' \in L'_C$}
-%		\State Add $ot$ into $C'$ to get a new tuple $C$;
-%		\State Add $C$ into $L_C$;
-%	\EndFor
-%\EndFor 
-%\State \Return $L_C$;
-%
-%\end{algorithmic}  
-%\end{algorithm}
-
+
+\def\inactive{\{-\}}
 \paragraph{Combining:}
-\QIN{
-The combining method enumerate all the possible status of the subnets.
-The result of the method hence call the combination as it present as all the possible combinations of their open transitions.
-Assume that there is a collection of $n$ subnets $L = {s_1, s_2, ..., s_n}$, if we notate $ot$ to be the set of open transitions of the subnet $s$ and $\eta$ means the subnet is not involved. 
-Then the combination $\texttt{COMB}$, a set of n-tuples, can be computed as an outer product of sets : 
-\[\texttt{COMB} : (\eta\cup ot_1) \times (\eta\cup ot_2)\times ... \times (\eta\cup ot_n) .\]
-}
+The combining method enumerate all the possible behaviours of the
+subnets, as all the possible combinations of their open transitions.
+Assume that there is a collection of $n$ subnets $L = {s_1, s_2, ...,
+  s_n}$, if we notate $ot_i$ to be the set of open transitions of the
+subnet $s_i$ and ``$-$'' means the subnet is not involved.  
+Then the combination $\texttt{COMB}$, a set of n-tuples, is the
+cartesian product of sets :  
+\[\texttt{COMB} : (\inactive\cup ot_1) \times (\inactive\cup ot_2)\times ... \times (\inactive\cup ot_n) .\]
+
 %Algorithm 2 shows the combining algorithm for enumerating all possible
@@
 \paragraph{Matching:}
-\QIN{$Given a synchronization vector ~ SV_k\in SV = (a'_i)^{i\in I} (b'_j)^{j\in J}\rightarrow v' , G_k , k\in K$, and a tuple
-$C_n\in \texttt{COMB} = {(v_i)}^{i\in I} , n\in N$ where $K$ and $N$ are the indices of the set elements.
-As the behavior of subnets should match with the synchronization vector to compose the subnets.
-The matching method tries matching $SV_k$ and $C_n$ to generate the predicates.
-According to the definition of predicate, the hole behaviors $Hole$ and result action $v$ are also involved. 
-}
-
-\QIN{
+The next step, for each synchronisation vector, and each possible
+combination of behaviour of the subnets as generated by the \emph
+{Combining} method, consists in building the combined predicate,
+and the corresponding open transition.
+From a synchronization vector
+$sv_k\in SV = (a'_i)^{i\in I} (b'_j)^{j\in J}\rightarrow v'$
+and its guard $G_k$, a tuple of open transitions
+$C_n\in \texttt{COMB} = {(v_i)}^{i\in I}$, the hole behaviors $Hole$,
+and a fresh variable representing the result action $v$, we build the
+predicate:
+
 $$Matching(SV_k, C_n, Hole, v) = 
@@
 \end{array}$$
-which is exactly the new part of predicate for one possible result.
-}
 
 \paragraph{Filtering:}
-\TODO{Eric: 3 levels of filtering, explain our choice}
+There may be several reasons why such a matching would fail:
+\begin{itemize}
+  \item if some subnet is marked as inactive in the vector, and the
+    chosen combinaison has an active behaviour at this position,
+  \item if some subnet action expression in the vector does not match (by
+    pattern-matching) the corresponding behaviour $C_n$,
+  \item or if the whole set of active subnet actions in the vector
+    cannot be matched (by unification) with the set $\{C_n\}$.
+\end {itemize}
+
+Each of these possible failures is more precise than the previous
+ones. But even when unification succeeds, it is still possible that
+the resulting predicate would be unsatisfiable, because of some
+incompatibility involving the guards. In our algorithm, we choose to
+apply only the simplest filter inside the \emph{Matching} method. All
+the rest will be checked later, using the satisfiability ckeck in the
+SMT engine.
 
@@
 using name generation using a global counter as a suffix.
-\subsection{Filtering the behaviour combinations}
-\QIN{There is already able to filter some wrong open transitions during the matching.
-We can ensure that the synchronization vector is not matched with the subnets if there is only one side not involved.
-Then we can remove the transitions from the result of matching according to the condition $\gamma$ where
-$\gamma = \bigcup_{i\in I}(v_i\in\eta\land a'_i\in\eta)\lor(v_i\in\eta\land a'_i\in\eta) .$
-}
+
 \subsection{Translation to SMTlib input language}

### 2018-01-15 2017-Xudong-SMT/FM-2018-extended.tex
new OT ex

--- 2018-01-15 2017-Xudong-SMT/FM-2018-extended.tex
@@
 \item[$\bullet$] $S_j \subseteq \AlgA$ is a set of action terms,
-  denoting the $\Sort$\footnote{The formal definition of $Sorts$ (set of actions of a Hole
-  or pNet), $Leaves$ and $Holes$ (all pLTSs (resp holes) in a pNet
-  hierarchical system. These can be found in \cite{henrio:Forte2016}.}
+  denoting the $\Sort$\footnote{The formal definition of $Sorts$ (the
+    set of actions of a Hole  
+  or pNet), and also of $Leaves$ and $Holes$ (respectively all pLTSs
+  and all holes in a pNet), can be found in \cite{henrio:Forte2016}.}
   of hole $j$.
@@
 
-The semantics of open pNets will be defined  as an open automaton. An open
-automaton is an automaton where each transition composes transitions
+The semantics of open pNets will be defined as an open automaton,that
+is an automaton where each transition composes transitions 
 of several LTSs with the
@@
 \begin{example}\emph{An open-transition.}
+  \TODO{a short explanation}
   \label{OT:lotos-composed}
-%
-%The \texttt{LOTOS} pNet of Fig. \ref{schema:lotos-pnet} has 2
-%controllers and 2 holes. We will show its full open Automaton in
-%section \ref{section:full-result}. We give one of its transitions here:
-%
-% \smallskip
-% $ ot_2  = \openrule{
-%                       \{0 \xrightarrow{\delta}_{C_1} 0, 0 \xrightarrow{acc(x)}_{C_2} 1\}, ~~
-%                       \{\xrightarrow{hb_{12}}_P\}, ~~ 
-%                        [s_0=0 \!\land\! hb_{12}=\delta(x)], ~~ 
-%                       \{s_0 \xleftarrow{} 1\}     
-%                      }
-%     {\ostate{00} \xrightarrow{\underline{\delta(x)}} \ostate{01}}$
+        \begin{mathpar}
+	\inferrule*[myfraction=\reddottedrule]
+	{\{s0~{\xrightarrow{fail(true)}} ~s1, t0~{\xrightarrow{start(true)}} ~t1\}
+	  \{\xrightarrow{hb}\}, hb=fail(true) \land v=\underline{fail}, \{t := 4\}
+        }
+	{<s0,t0> \xrightarrow {v} <s1,t1>}
+	\end{mathpar}
 \end{example}
@@
 \paragraph{Structural Semantic Rules:}
-\TODO{Do we push the rules in the appendix, and leave only a short high
-  level desciption here ?}
-
-Now we build the semantics of an open pNet as an open automaton where
+\TODO{I have pushed the rules in the appendix, we need to add a short high
+  level desciption here.}
+
+\TODO{ERIC: I choose here to remove the expample of construction of an
+  OT as a deduction tree. First because it was already published in
+  the Forte'16 paper, but also because it is not the way the algorithm
+  is working.}
+
+%% \begin{example} \emph{Using the operational rules to compute  open-transitions: }
+%%   in Fig. \ref{usingrules:ot2} we show the deduction tree used to construct and prove the 
+%%   open transition $ot_2$.
+%% \end{example}
+
+%% \begin{figure}[h]
+%% %  \vspace{-10mm}
+
+%% \begin{mathpar}
+%%   \small
+%%   \inferrule
+%%     {
+%%           \inferrule
+%%               {0 \xrightarrow {\delta}_{C_1} 0 ~~
+%%                [ s_0=0 ]
+%%               }
+%%               {C_1
+%%                 \models
+%%                 \openrule
+%%                       {0 \xrightarrow{\delta}_{C_1} 0 ~~
+%%                        [ s_0=0 ] ~~
+%%                        \{ s_0 \leftarrow 1\}
+%%                       }
+%%                       {\ostate{0}\xrightarrow{\delta}\ostate{0}}
+%%               }
+%% 	\\
+%%       \inferrule
+%%         {
+%%           \inferrule
+%%               {0 \xrightarrow{acc(x)}_{C_2} 1}
+%%               {C_2
+%%                 \models
+%%                 \openrule
+%%                       {0 \xrightarrow{acc(x)}_{C_2} 1}
+%%                       {\ostate{0}\xrightarrow{acc(x)}\ostate{1}}
+%%               }
+%%         }
+%%         {
+%%           \textrm{acc(x);Q}\models
+%%               \openrule
+%%                   { 0 \xrightarrow {acc(x)}_{C_2} 1}
+%%                   {\ostate{0}\xrightarrow{acc(x)}\ostate{1}}
+%%         }   
+%%     }
+%%     {
+%%      \textrm{PN1}
+%%      \models
+%%         \openrule{
+%%                         0 \xrightarrow{\delta}_{C_1} 0, 0 \xrightarrow{acc(x)}_{C_2} 1 ~~
+%%                        \{\xrightarrow{hb_{12}}_P\} ~~ 
+%%                         [s_0=0 \!\land\! hb_{12}=\delta(x)] ~~ 
+%%                        \{s_0 \xleftarrow{} 1\}           
+%%                       }
+%%      {\ostate{00} \xrightarrow{\tau} \ostate{01}}
+%%       }\vspace{-4ex}
+%% \end{mathpar}
+%%   \caption{Proof of  $ot_{2}$ (interaction of process $P$ and action $acc(x)$) for ``P>>(acc(x);Q)''}
+%%   \label{usingrules:ot2}
+%% \end{figure}
+
+%% The proof tree uses TR1 twice, for the $\delta$ transition of $C_1$
+%% and for the $acc(x)$ transition of $C_2$, then uses an action
+%% $hb_{12}$ of hole $P$, and combines the results using the first vector
+%% of the PN2 sub-pNet, and the second vector of the top node according
+%% to TR2. This yields a final $\underline{\delta(x)}$ transition. The
+%% deduction tree in the figure shows how the predicates are generated in
+%% this process.
+
+\section{Generation of Open Automata}
+\label{section:implementation}
+In this section we describe the algorithm implementing the pNet
+semantics, the interaction with the Z3 SMT solver, and we show the
+result on our  example.
+
+Our algorithm starts with an open pNet, and builds its set of open
+transitions (OTs). Its main loop is a classical residual algorithm: starting
+from the initial global state, it pick a state in an unexplored set, and
+computes all possible OTs, adding their target states in the
+unexplored set, until this set is empty. As the potential set of
+global states is finite (see \cite{henrio:Forte2016}), this terminates.
+
+The inside loop (\emph{MakeTransitions} method) applies recursively
+the semantic rules following the structure of the pNet. 
+For pLTS at leaves, rule Tr1 simply take the pLTS transitions of the
+corresponding local state and build the predicate to generate the
+open transition. 
+On a pNet node to apply rule Tr2 we use two methods, combining and
+matching, to generate the new predicate of the open transitions in a
+hierarchical manner.
+
+Last, at the root of the pNet, the predicate of each OT is translated
+into SMTlib assertions, and checked for satifiability. Unsatisfiable
+OTs are pruned, and the final open automaton is computed as the set of
+global states reachable by satisfiable OTs.
+
+\begin{algorithm}
+\caption{Open Automaton Generation}
+\begin{algorithmic}[1]
+\Require The pNet node P.
+\State Initialize sets $U$, $E$ for unexplored/explored global states, $L$ for result OTs;
+\While{!isEmpty(U)}
+	\State Chose $S$ in $U$;
+	\State OT = MakeTransitions(P, S);
+        \State Store $OT$ in $L$; 
+	\For{each target global state $T$ from $OT \in L$}
+		\IfThen{$(!U.contains(T))\ \&\&\ (!E.contains(T))$}{Add $T$ into the $U$;}
+	\EndFor
+\EndWhile
+\State Prune the open transitions in $L$ using the SMT solver;
+\State \Return $L$;
+
+\end{algorithmic}  
+\end{algorithm}
+
+\begin{algorithm}
+\caption{MakeTransitions()}
+\begin{algorithmic}[1]
+\Require The pNet node P; The start global state S.
+\State Initialize a list $l$, $L$ for sub-transitions/transitions.
+	\For{each Subnet in P}
+	\\ ~~~ $\setminus \setminus$ Recursively applying Tr1 or Tr2 on the sub-nodes.
+                \State Store MakeTransitions(Subnet, S) in $l$;
+	\EndFor
+	\For{each $sv \in SV$}
+		\State $comb = Combining(l)$;
+                 \State $ot = Matching(sv, comb, hole, v)$;
+                 \State Store $ot$ in $L$; 
+	\EndFor
+\State \Return $L$;
+\end{algorithmic}  
+\end{algorithm}
+
+%
+%For holes, their behavior is unspecified, it doesn't have an exact
+%external presentation of action. We only give an action variable to each hole
+%and treat it as hole behavior to suppose working status of the
+%hole.
+%% Here should have a constraint that this variable belongs to the sort of hole.
+%In every case, the hole behaviors are unchanged, so we
+%only make the combinations of subnets' open transitions. 
+%
+
+\def\inactive{\{-\}}
+\paragraph{Combining:}
+The combining method enumerate all the possible behaviours of the
+subnets, as all the possible combinations of their open transitions.
+Assume that there is a collection of $n$ subnets $L = {s_1, s_2, ...,
+  s_n}$, if we notate $ot_i$ to be the set of open transitions of the
+subnet $s_i$ and ``$-$'' means the subnet is not involved.  
+Then the combination $\texttt{COMB}$, a set of n-tuples, is the
+cartesian product of sets :  
+\[\texttt{COMB} : (\inactive\cup ot_1) \times (\inactive\cup ot_2)\times ... \times (\inactive\cup ot_n) .\]
+
+%Algorithm 2 shows the combining algorithm for enumerating all possible
+%working status combinations from subnets. Dealing with a list $TR$
+%containing  sets of open transitions from different subnets,
+%the algorithm choses one of sets $L_{ot}$ and does combining on the
+%remaining part of $TR$ recursively. The case when a subnet is not working is
+%managed by adding a $null$ into the $L_{ot}$.
+
+\paragraph{Matching:}
+The next step, for each synchronisation vector, and each possible
+combination of behaviour of the subnets as generated by the \emph
+{Combining} method, consists in building the combined predicate,
+and the corresponding open transition.
+From a synchronization vector
+$sv_k\in SV = (a'_i)^{i\in I} (b'_j)^{j\in J}\rightarrow v'$
+and its guard $G_k$, a tuple of open transitions
+$C_n\in \texttt{COMB} = {(v_i)}^{i\in I}$, the hole behaviors $Hole$,
+and a fresh variable representing the result action $v$, we build the
+predicate:
+
+$$Matching(SV_k, C_n, Hole, v) = 
+\begin{array}{l}
+\forall {(a'_i)}^{i\in I},
+{(b'_j)}^{j\in J},v'.
+\\
+v_i=a'_i\land \, b_j=b'_j \land v=v' \land G_k
+\end{array}$$
+
+\paragraph{Filtering:}
+There may be several reasons why such a matching would fail:
+\begin{itemize}
+  \item if some subnet is marked as inactive in the vector, and the
+    chosen combinaison has an active behaviour at this position,
+  \item if some subnet action expression in the vector does not match (by
+    pattern-matching) the corresponding behaviour $C_n$,
+  \item or if the whole set of active subnet actions in the vector
+    cannot be matched (by unification) with the set $\{C_n\}$.
+\end {itemize}
+
+Each of these possible failures is more precise than the previous
+ones. But even when unification succeeds, it is still possible that
+the resulting predicate would be unsatisfiable, because of some
+incompatibility involving the guards. In our algorithm, we choose to
+apply only the simplest filter inside the \emph{Matching} method. All
+the rest will be checked later, using the satisfiability ckeck in the
+SMT engine.
+
+\subsection{Management of state variable assignments}
+%The pLTS contains some variables in each of its states (state
+%variables), or just as global states of the pLTS (global variables).
+%Both can be assigned in the pLTS transitions.
+%The algorithm composing assignments from subnets is different from the
+%generation of predicates. 
+%%When applying Tr1, we just keep the
+%%assignments in the Post of the open transition. And when it comes to
+%%Tr2, Post is the union of the assignments propagate from the
+%%subnets. 
+%The assignments provide value of the variables in
+%predicates. There is usually not only one assignment for a state variable as
+%several incoming transitions of a state can perform different
+%assignments on the same variable. The values of the
+%variables are necessary for checking satisfiability of the open
+%transitions together with predicates, miss of them may drop the
+%unsatisfiable results. In order to avoid such mistakes, the algorithm
+%manages the variables together with a list.
+%
+%The list we used contains triples $<v,\ S, \ AssignRH>$ set for each pLTS to record
+%the information of both state and global variables of the pLTS where $v$ is the variable in pLTS, $S$ is its owner state and $AssignRH$ is a list of expressions over other variables in the right hand side of assignments of $v$.
+The $S$ can be $null$ in the record triple, it means the variable is global in the pLTS belonging to all the states.
+%%So it should be noted that the changing of the value of the global state variable every time a transition is conducted.
+$AssignRH$ is the collection of all the possible expressions coming from the the right hand side of assignments.
+It keeps the information of the assignments for each variable.
+%We update the list of record triples every time Tr1 is applied, adding the right side of the assignments into corresponding expression lists.
+So the list keeps the all the assignments in the pLTS.
+Then we can track all the possible value of the variables when computing open transitions.
+%The initial value of the state variable is also seen as an assignment
+%for that variable. We must give a initial value to the global state
+%variable or there will be some problem in the start state. However, we
+%sometimes don't give initial values to the state variables (except the
+%global variables) as their initial values are decided by their first
+%assignments. Checking whether each variable is initialized before
+%being used is a separated problem, that should be done before starting
+%our algorithm.
+
+In a pLTS, there may be several incoming transitions of some states
+that assign potentially different values to a state variable.
+To handle such cases, the algorithm manages the variables together
+with a list for each pLTS.
+The list we used contains several triples <$v$, $S$, $AssignRH$> 
+where $v$ is the variable in pLTS, $S$ is its owner state and
+$AssignRH$ is a list of expressions over other variables in the right
+hand side of assignments of $v$.
+As a pragmatic extension to the formal definition, we also manage
+``global variables'', defined in all states of the pLTS.
+
+%There are some assignment on the variables in each of states of the pLTS (state variables), or just as global states of it (global variables).
+There is usually not only one assignment for a state variable, miss of them may drop the unsatisfiable results.
+In order to avoid such mistakes,
+
+%% \QIN{
+%% The list we used contains several triples <$v$, $S$, $AssignRH$> to
+%% record the information of both state and global variables of the pLTS,
+%% where $v$ is the variable in pLTS, $S$ is its owner state and
+%% $AssignRH$ is a list of expressions over other variables in the right
+%% hand side of assignments of $v$. It means the variable is global in
+%% the pLTS belonging to all the states, if $S$ is $null$. We update the
+%% list of record triples every time Tr1 is applied. Then we can track
+%% all the possible (symbolic) value of the variables when computing open transitions.
+%% }
+
+\subsection{Pruning the unsatisfiable results}
+\label{section:pruning}
+%We have used a brute-force method to generate all the possible open
+%transitions in the open automaton. It obviously contains some of
+%unsatisfiability in the open transitions. In
+%Fig~\ref{schema:unsat-ot}, we display an unsatisfiable open transition
+%from the result of the CCS running example. It shows the case that the
+%top level transmits out the action from the PN2, formula $a.P$, as
+%this time only PN2 is working and C1 is performing action $a$ when
+%hole $P$ is also working. When matching this case against the second
+%synchronization 
+%vector of PN2, transmitting the behavior from hole $P$ to the higher
+%level, is used while it is obviously violate the guard of the
+%vector. So we can easily find the contradiction between the generated
+%predicate term $ra:152:1=l \!\land\! a=:ra:152:1$ and the guard
+%composed into the predicate $a \neq l$.
+
+\begin{figure}[h]
+%$\begin{array}{@{}r@{}l@{}}
+%%{s0---a-->s1},   {---:hb:15:2-->},   (:ra:15:2 = act:sva:1:3)/\(:ra:152:1 = l)/\(a = :ra:152:1)/\(l!= a)/\(:hb:15:2 = y:sva:15:2)/\(:ra:15:2 = y:sva:15:2)/\(y:sva:15:2 != l)/\(:ra:1:3 = act:sva:1:3)
+%    ot  = &\openrule{\{0 \xrightarrow{a} 1\}, ~~\{\xrightarrow{:hb:15:2}\}, ~~:ra:15:2=act:sva:1:3 \\
+%    \OTland:ra:152:1=l \OTland a=:ra:152:1 \OTland a \neq l \OTland :hb:15:2 = y:sva:15:2 \\
+%    \OTland :ra:15:2 = y:sva:15:2  \OTland y:sva:15:2 \neq l \OTland :ra:1:3 = act:sva:1:3}
+%    {\ostate{00} \xrightarrow{:ra:1:3} \ostate{10}}\\
+%  \end{array}$
+%\caption{One of the unsatisfiable open transitions in CCS running example}  \label{schema:unsat-ot}
+%\end{figure}
+
+%{s0---delta-->s0},   {---:hb_P:12:1-->},   (:ra:11:1=l)/\(delta=:ra:11:1)/\(var_s0=0)/\(:hb_P:12:1=a1:sva_SV0:1:1)/\(:ra:1:1=a1:sva_SV0:1:1)/\(a1:sva_SV0:1:1!=delta(x)),   {var_s0 := 1}
+$\begin{array}{@{}r@{}l@{}}
+    ot  = &\openrule{\{0 \xrightarrow{\delta} 0\}, ~~\{\xrightarrow{:hb:12:1}\}, ~~\OTvar{:ra:11:1}=l \OTland \delta=\OTvar{:ra:11:1} \OTland \OTvar{s0}=0 \\
+     \OTland \OTvar{:hb:12:1}=\OTvar{a1:sva:1:1} \OTland \OTvar{:ra:1:1}=\OTvar{a1:sva:1:1} \OTland \OTvar{a1:sva:1:1} \neq \delta(x), ~~\{\OTvar{s0} \leftarrow 1\}}
+    {\ostate{00} \xrightarrow{\OTvar{:ra:1:1}} \ostate{00}}\\
+  \end{array}$
+\caption{One of the unsatisfiable open transitions in LOTOS running example}  \label{schema:unsat-ot}
+\end{figure}
+
+We use a brute-force method to generate all the possible open
+transitions in the open automaton, using all possible combinations of
+synchronization vectors. Naturally this builds some transitions where
+the predicates express incompatible constraints. Even if having an
+unsatisfiable (symbolic) transition in the open automaton would not be incorrect,
+we want to check them for satisfiability, and reduce the number of
+transitions and states in the automaton.
+\TODO{Change...} In Fig.~\ref{schema:unsat-ot}, we display an example of an
+unsatisfiable open transition 
+from the result of our example. It shows the case where
+the controller C1 wants to move the control from $P$ to $(acc(x);Q)$,
+conducting a $\delta$ transition. However, a synchronization
+vector is chosen that does not match with this action, and we can
+easily find the contradiction in the 
+generated predicate term ``$\OTvar{:ra:11:1}=l \!\OTland\! \delta=\OTvar{:ra:11:1}$''.
+
+Checking satisfiability requires some symbolic computation
+on the action expressions and the predicates, and this 
+may depend on the specific theory of the action algebra. 
+We use the SMT solver Z3 to check the predicate of the result open transitions, 
+it will return whether the predicate is satisfiable or not.
+The ``Modulo Theory'' part of SMT solvers is important here, so that
+the solver can use specific properties of each action algebra.
+
+\begin{figure}[t]
+  %  \centerline{\includegraphics[width=12cm]{XFIG/SMTLIB2}}
+    \centerline{\includegraphics[width=\linewidth]{XFIG/SMTLIB2}}
+  \caption{The input of the Z3 solver in SMT-LIB language and the output result}  \label{schema:smt-lib}
+\end{figure}
+
+%% \begin{figure}[t]
+%%   \centerline{\includegraphics[width=10cm]{XFIG/Interaction}}
+%%   \caption{The architecture of the interaction between pNet API and Z3}  \label{schema:interaction}
+%% \end{figure}
+
+\subsection{Translation to SMTlib}
+
+\TODO{Eric: Replace by (excerpts of) the formal version, from appendix, and reduce to less than one page}
+
+\paragraph{Presentation of algebra}
+
+As seen in section
+\ref{section:pnets}, the \emph{term algebra} used to express the
+action expressions and data parameters is left open in
+the pNet definition.
+
+So, for a given language, we now need to specify its data and action
+domains, giving them an abstract syntax (sorts, constructors, operators,
+and predicates). We call this a \emph{Presentation}.
+We also define a concrete syntax, that will be used for
+pretty-printing, but also for translating the presentation, and the
+predicates, into Z3 syntax (see the ``declare-datatypes'' statement in
+Fig~\ref{schema:smt-lib}).
+
+An algebra presentation contains:
+
+\begin{itemize}
+	\item Sorts: Constants sets of the algebra or types of the data
+          and actions (integer and boolean sort are implicitly
+          declared).  There \emph{must} be one sort for actions, and
+          eventually others for the types of data
+          parameters. In the LOTOS example, 
+          we have the $Action$ sort: $\OTvar{Action = } \{ l, \delta,
+          r, p, q, acc \} .$
+
+	\item Operators:
+          %Operators used to construct action expressions; they are
+          constructors and predicates for data and action sorts. For
+          instance, in our LOTOS example, we
+          have a generic action constructor ``$ACT$'', taking as
+          argument an action litteral and a data parameter, declared as:
+          $\OTvar{ACT:}\OTvar{< Action, Data >} \rightarrow \OTvar{Action.}$, 
+        \item Constants: The satisfiability solver need to know which
+          actions in the pLTS behaviors are constants (like the $l$, $\delta$, 
+          $r$ of the controllers in running example). 
+          For a given pNet system, the sort $Action$ will include all
+          these constants.
+\end{itemize}
+
+\paragraph{Interaction with Z3}
+%\TODO{1. example input of Z3 in SMT-LIB.[DONE] 2. software architecture.[DONE]}
+%There are several ways to interact with the Z3 solver. 
+%It is possible to use Z3 interactively using the SMT-LIB
+%(Python-based) language. 
+From inside our algorithm code, we submit satisfiability requests to
+Z3 using its JAVA API. Here for readability, we
+show the Z3 code using its SMT-LIB input language. As an
+example in
+Fig~\ref{schema:smt-lib}, we show the input for checking the
+transition of Fig.~\ref{schema:unsat-ot}. It contains the declaration
+of the LOTOS action algebra types 
+and constructors, then the declaration of variables, and finally the
+predicate to be checked, encoded as a set of assertions.
+%% Generally, some $datatypes$ are declared to input the sorts, while here
+%% we only declare one $datatypes$ named $Action$ to involve all the
+%% constant actions. Then we input the predicate of this open transition
+%% in two parts: the variables contained in the predicate are declared
+%% first, then the terms of predicate are inputed as $assertions$ one by
+%% one. 
+The result "unsat" in the output is just what we expected.
+
+%\TODO{edit the figure to make it smaller in height [DONE]}
+
+%We present the architecture of the interaction with Z3 in
+%Fig~\ref{schema:interaction}.
+%For each OT generated at the toplevel of a pNet, the predicate must be
+%submitted for satisfiability check to Z3. For that we need to
+%translate into Z3 (Java-API) syntax, both the elements of the action
+%algebra, and the predicates itself, including the encoding of the
+%variable assignments (the Post part).
+%
+%The $presentation$ of the action algebra
+%is declared at the beginning of the algorithm as the $sorts$ and the
+%$operators$ will be used throughout the whole algorithm. It is
+%translated into $datatypes$ and $functions$ then submitted to the Z3
+%at the same time. Each candidate predicate will then be translated
+%into $assertions$ before submitted to Z3 after the algorithm
+%computing out all the possible open transitions, they act as
+%intermediate results there. Together with the $datatypes$ and
+%$functions$, the $assertions$ are used to check the satisfiability of
+%the predicate in Z3.
+
+To build the input submitted to Z3 for each OT,
+we translate the algebra $presentation$, the predicates and the
+variable assignments (the Post part) into Z3 (Java-API) syntax.
+% The $presentation$ and the predicates are translated separately.
+
+\paragraph{Translation of Action algebra presentation}
+\TODO{Exerpt of the formalisation}
+The $datatypes$ are declared according to the $sorts$ the users
+declared in the $presentation$. If the return type of the $functions$
+is one of the $datatypes$, we add this $function$ to the $datatypes$ declaration.
+So when we declare the operator ACT we illustrated in section 4.1, it
+will be just declared together with the constants like :\\
+\centerline{$\OTvar{(ACT\ (action3\ Action)(data\ Int))}$}
+
+The $functions$ can also be declared independently, it usually applies to functions returning integer or boolean, in the format like:\\
+\centerline{$\OTvar{(declare\text{-}fun\ MAX\ (Int\ Int)\ Int)}$}
+
+%Although in Fig~\ref{schema:smt-lib} we have not declared $functions$ outside of $datatypes$, there still exists $functions$ declared independently.
+The input and output types of the $function$ are also determined by the construct of the  $operators$ in the presentation.
+For example, we define a new operator to present the equation between two actions in LOTOS example $\text{EQUAL}$ in the format likes:
+%
+%\[EQUAL: \quad < Action , Action > \rightarrow Bool .\]
+%
+%It will be translated into the Z3 statement: 
+%
+%\[\text{(declare-fun\ EQUAL\ (Action\ Action)\ Bool) .}\]
+
+\paragraph{Translating assignments into predicate terms}
+\TODO{Exerpt of the formalisation}
+
+%The assignments are also taken into account when checking the
+%satisfiability of the open transitions as they represent the value of
+%the variables involved in an OT. In order to do that, we employs a
+%translation from assignments into term of predicates. The assignments
+%required to be translated are only those belong to the variables
+%contain in the start states of the open transitions. The assignments
+%are represented as equations between the variables and the expressions
+%on the right side of assignment. For the assignments of the same
+%variable, we do not figure out which state is the precursor of current
+%state, we keep all these possible equations instead, and generate the
+%disjunction of these equations. The state could always move to the
+%target state if there exists one of the values of its variable
+%satisfies the guard.
+%%\TODO{It won't matter the variable of the next state
+%%except that the right hand side expression contain its variables. This
+%%is a problem left to be solved in our future work. WHICH PROBLEM ?}
+%After that, for the assignments of the different variables, we generate a conjunction of them. This way we obtain a new term of the predicate involving assignments of the variables.
+
+State-variable assignments are also treated as a part of the
+predicates when checking the satisfiability. % Here we need conduct some
+% translations,
+For each assignement in a $\Post$ predicate, such as $\{s_0 \leftarrow 1\}$ in section
+~\ref{section:op-semantics}, we translate it into an equation
+$s_0=1$. For several assignments of the same variable in the same state,
+we generate the disjunction of 
+these equations. Correspondingly, we generate a conjunction for the
+assignments from different variables.
+
+\paragraph{Checking satisfiability}
+
+% We check the satisfiability of open transitions on the top level of
+% the pNet, treating these open transitions as the intermediate result
+% of the algorithm. After we get the intermediate results of open
+% transitions, we check them one by one.
+Here we declare first all the variables in the predicates, with their
+sorts.
+An example of syntax is::\\
+\centerline{$\OTvar{(declare-const\ |:ra:1:1|\ Action)}$}
+
+\noindent Then each term of the
+predicate is an assertion in Z3, as an example, in the former
+unsatisfiable result in Fig~\ref{schema:unsat-ot}, the contradiction is occurred in terms: \\
+\centerline{$\OTvar{(:ra:11:1=l)} \OTland \OTvar{(delta=:ra:11:1)}$}\\
+from which we generate the following two assertions:\\
+\centerline{$\OTvar{(assert\ (=\ |:ra:11:1|\ l))\ \ \ (assert\ (=\ delta\ |:ra:11:1|))}$}
+
+\noindent The predicate submitted to the Z3 also contains the
+assignments encodings.
+In the case of $ot_2$, it
+gives the assertion:\\
+\centerline{$\OTvar{assert (or (= var\_s0 0) (= var\_s0 01)))}$}
+
+\subsection{Simplification of Predicates}
+\ERIC{: motivated, add refs, and an abstract presentation of stuff from pages 19-20}
+
+Before:
+  	\begin{mathpar}
+	\inferrule*[myfraction=\reddottedrule]
+	{\{s0~{\xrightarrow{fail(true)}} ~s1, t0~{\xrightarrow{start(true)}} ~t1\}
+	  \{\xrightarrow{hb}\},\\
+\qquad b1=true \land b2=true \land hb=fail(b0) \land b1=b2 \land (b1\cup b2
+\implies b0) \land v=\underline{fail}, \{t := 4\}
+        }
+	{<s0,t0> \xrightarrow {v} <s1,t1>}
+	\end{mathpar}
+
+After:
+          	\begin{mathpar}
+	\inferrule*[myfraction=\reddottedrule]
+	{\{s0~{\xrightarrow{fail(true)}} ~s1, t0~{\xrightarrow{start(true)}} ~t1\}
+	  \{\xrightarrow{hb}\}, hb=fail(true) \land v=\underline{fail}, \{t := 4\}
+        }
+	{<s0,t0> \xrightarrow {v} <s1,t1>}
+	\end{mathpar}
+
+\subsection{Result of the running example}
+\label{section:full-result}
+
+\TODO{Xudong: Update: we have 11 satisfiable OTs here}
+Our tool builds 30 open
+transitions, out of which 27 are detected unsatisfiable by Z3, we
+get only 3 results left; the resulting open automaton is shown in
+Fig. ~\ref{schema:lotos-result}, together with its open transitions.
+
+The resulting open transitions represent all the
+possible movements of the LOTOS example.
+What can be observed is any actions of the process $P$ from the beginning, until $P$ performs a $\delta(x)$ and the value of
+$x$ is transmitted to the $acc(x);Q$ giving out a silent action. Such behavior is performed by the $ot_1$ then $ot_2$. 
+Then it keeps presenting the behavior of $Q$, as seen in $ot_3$. 
+%The $ot_1$ transition means that the actions of the process $P$ could
+%be transmitted out, until $P$ performs a $\delta(x)$ and the value of
+%$x$ is transmitted, through transition
+%$ot_2$. The other 3 open transitions shows the behaviors of the
+%process $Q$ while the $ot_3$ and $ot_4$ won't be performed as the
+%controller has already set the value $s_0$ to 1 in the previous
+%action.
+
+\begin{figure}[t]
+   \centerline{\includegraphics[width=12cm]{XFIG/BIPresult-ArchFailureTimerMax}}
+   \caption{Open Automaton\TODO{syntax could be better...}}  \label{schema:resultOA}
+ \end{figure}
+
+\begin{figure}[h]
+%  \centerline{\includegraphics[width=5cm]{XFIG/LOTOSresult}}
+  \TODO{Detaisl of some OTs of the FailureTimer}
+
+$\begin{array}{@{}r@{}l@{}}
+    ot_1  = &\openrule{\{0 \xrightarrow{l}_{C_1} 0\}, ~~\{\xrightarrow{hb_{1}}_P\}, ~~[s_0=0 \!\land\! hb_{1} \neq \delta(x) \!\land\! v_1=hb_{1}]}
+    {\ostate{00} \xrightarrow{v_1} \ostate{00}}\\
+  \end{array}$
+
+$\begin{array}{@{}r@{}l@{}}
+    ot_2  = &\openrule{\{0 \xrightarrow{\delta}_{C_1} 0, 0 \xrightarrow{acc(x)}_{C_2} 1\}, ~~\{\xrightarrow{hb_{2}}_P\}, ~~[s_0=0 \!\land\!
+hb_{2}=\delta(x) \!\land\!
+v_2=\underline{\delta(x)}], ~~\{s_0 \xleftarrow{} 1\}}
+    {\ostate{00} \xrightarrow{v_2} \ostate{01}}\\
+  \end{array}$
+
+\caption{The open automaton of the LOTOS formula}  \label{schema:lotos-result}
+\end{figure}
+
+%\subsubsection{Result of CCS example}
+%\QIN{
+%also can present all the possible behavior of that CCS formula with 16 open
+%transitions in Fig. ~\ref{schema:ccs-result}, here we omitted the details of open transitions. 
+%In this example, there are 32 more transitions detected unsatisfiable by Z3.
+%}
+%
+%\QIN{
+%Here we only show one of the result transitions. It presents the value-passing between $a.P$ and $b.Q$ and they are synchronized then
+%give out an silent action $\tau$, process $P$ and $Q$ should not work in this case.
+%}
+%
+%\begin{figure}[h]
+%  \centerline{\includegraphics[width=5cm]{XFIG/CCSresult}}
+%  
+%  $\begin{array}{@{}r@{}l@{}}
+%    ot_1  = &\openrule{\{0 \xrightarrow{a}_{C_1} 1, 0 \xrightarrow{b}_{C_2} 1\}, ~~a=!ch_{11}(v_{11}) \!\land\! b=?ch_{11}(v_{11}) \!\land\! a\neq l \!\land\! b\neq r\!\land\! v_1=\tau}
+%    {\ostate{00} \xrightarrow{v_1} \ostate{11}}\\
+%  \end{array}$
+%  
+%\caption{The open automaton of the CCS parallel formula}  \label{schema:ccs-result}
+%\end{figure}
+
+%% \QIN{
+%% To sum up, from the pNets encoding the formulas of given algebra, which inputed by the user, we can exactly construct
+%% the open automaton for them. 
+%% }
+
+\section{Conclusion and Discussion}
+\label{section:conclusion}
+
+In this paper we presented the algorithm for generating an open
+automaton representing the semantics of an open pNet, and we described
+the implementation of the
+algorithm. Our implementation includes two main parts. First, we
+compute all the possible open transitions. The actions in pLTS and
+hole behaviors are composed in the algorithm while the generation of
+predicate need to match the combinations of the subnets with the
+synchronization vectors. Some of the open transitions obtained at this
+intermediate step, constructed in a structural manner from all
+possible combinations of possible logical predicates, may
+contain predicates which do not represent any possible concrete
+instantiations. 
+To get rid of these useless transitions, we use the SMT solver Z3 for checking the
+satisfiability of the predicate in each open transition. In
+order to do that, we encode into Z3 the action algebra presentation,
+the a representation of the predicates, before submitting them to the
+Z3 solver. We implemented our algorithm in the VerCors platform and use some
+running examples, encoding expressions from various process algebras, to test the
+algorithm. Our use-cases show that our encoding
+identifies successfully all unsatisfiable open transitions and that
+the resulting automaton reflects correctly the expected 
+movements of the encoded process expressions.
+
+Among the questions arising during this work, an important one is the
+efficiency of Z3 for our needs. Z3 is famous for being very fast for
+solving very large sets of assertions, and this could be important for
+us. But we encountered  some problems during the implementation the
+checking method using Z3. For example, if the $functions$ and the
+$datatypes$ part of the algebra presentation we submit to the solver
+are independent with each other, then checking the $assertions$ is a
+simple work. However, $functions$ on recursive $datatypes$ make it
+more complex, some special rules might be defined by user for the
+induction. Also, we need more evidence that dealing with more complex
+action algebras, that would involve axiomatizing their data structures
+into Z3 theories, will indeed allow us to decide validity of
+predicates.
+We may also try other automatic theorem provers, depending on the structure of the proofs we need.
+
+\TODO{Change perspective: we are working on the formal extensino of
+  BIB architectures, and their semantics in terms of pNets. Then
+  bisimulation and model-checking principles adapted to open pNet
+  systems are under development}
+
+Naturally, our next goals after the generation of the open automata
+will be to model-check, and to check equivalence of  pNets. While
+model-checking open automata (with a suitable logic including
+predicates on data) seems easy to define, equivalence checking is more challenging.
+In previous paper, we
+have already found the FH-bisimulation, inspired by~\cite{deSimone85} as a
+suitable definition. But usual approaches of bisimulation by partition
+refinement does not work easily with symbolic transitions. In a first
+step we may want instead to define and implement an algorithm for
+checking that a given equivalence relation between open automata 
+states is indeed a FH-Bisimulation. Finding automatically a
+bisimulation relation or the most general bisimulation will be more
+challenging. It appears also that when comparing different pNets with
+different structure, strong bisimulation will be too strong a notion,
+and that we will have to define proper notions of weak equivalence or
+refinements.
+
+Before that work, we need to reconsider the result open transitions
+from our algorithm. The ideal
+result that we showed in the bottom part of
+Fig.~\ref{schema:lotos-result} is not the one generated by the algorithm,
+because the original one contains many intermediate
+variables, such as fresh local variables of synchronization
+vectors, and fresh result variables of intermediate open transitions.
+Such intermediate variables come from the way predicates are
+generated, and depends on the particular structure of the pNet. But
+they are not significant in the resulting behavior, and should be
+eliminated before comparing such behavior with another pNet.
+To eliminate the intermediate variables in the predicate, we want to define
+the set of the significant variables that we won't eliminate: the
+local variables of pLTS transitions, the hole behaviors and the result
+action at the top level.
+The result of the elimination will be simpler predicates, that can be
+successfully compared (e.g. by Z3) within the bisimulation checking
+algorithm.
+
+\bibliographystyle{lncs/splncs}
+
+% \bibliography{oasis,biblio}
+\bibliography{biblio}
+
+% \newpage
+\appendix
+
+\section{pNet semantic rules}
+
+\paragraph{Note:} For convenience, we have included here the semantic rules for pNets,
+that were already published in \cite{Forte}.
+
+We build the semantics of an open pNet as an open automaton where
 LTSs are the pLTSs at 
@@
 
-%
-%\begin{figure}[tb]
-%\begin{mathpar}
-%  \small
-%  \inferrule
-%    {\inferrule
-%      {
-%          \inferrule
-%              {1 \xrightarrow {l}_{C_1} 1}
-%              {C_1
-%                \models
-%                \openrule
-%                      {1 \xrightarrow{l}_{C_1} 1}
-%                      {\ostate{1}\xrightarrow{1}\ostate{1}}
-%              }
-%        }
-%        {\textrm{P}
-%          \models
-%            \openrule{
-%              1 \xrightarrow {l}_{C_1} 1,\,
-%              \{\xrightarrow{b_P}_P\},\, b_P\neq l}
-%                      {\ostate{1}\xrightarrow{b_P}\ostate{1}}
-%        }\\
-%%      \sm{fresh}v         \\
-%      \inferrule%*[right={L_1}]
-%        {
-%          \inferrule
-%              {0 \xrightarrow{b}_{C_2} 1}
-%              {C_4
-%                \models
-%                \openrule
-%                      {0 \xrightarrow{b}_{C_2} 0,\, b\neq r}
-%                      {\ostate{0}\xrightarrow{b}\ostate{1}}
-%              }
-%        }
-%        {
-%          \textrm{b:Q}\models
-%              \openrule
-%                  { 0 \xrightarrow {b}_{C_2} 1,\, \ b\neq r}
-%                  {\ostate{0}\xrightarrow{b}\ostate{1}}
-%        }   
-%    }
-%    {
-%     \textrm{PN1}
-%     \models
-%        \openrule{
-%                       1 \xrightarrow{l}_{C_1} 1 ~~
-%                       0 \xrightarrow{b}_{C_2} 1 ~~
-%                       \{ \xrightarrow{b_P}_{P} \}               ~~
-%                 [ a\neq l \land b\neq r \land b_P=?ch(v) \land b=!ch(v) ]              
-%                      }
-%     {\ostate{10} \xrightarrow{\tau} \ostate{11}}
-%      }\vspace{-4ex}
-%\end{mathpar}
-%  \caption{Proof of  $OT_{11}$ (with interaction of processes $P$ and action $b$) for ``a.P||b.Q''}
-%  \label{usingrules:OT11}
-%\end{figure}
-
-\begin{example} \emph{Using the operational rules to compute  open-transitions: }
-  in Fig. \ref{usingrules:ot2} we show the deduction tree used to construct and prove the 
-  open transition $ot_2$.
-\end{example}
-
-\begin{figure}[h]
-%  \vspace{-10mm}
-
-\begin{mathpar}
-  \small
-  \inferrule
-    {
-          \inferrule
-              {0 \xrightarrow {\delta}_{C_1} 0 ~~
-               [ s_0=0 ]
-              }
-              {C_1
-                \models
-                \openrule
-                      {0 \xrightarrow{\delta}_{C_1} 0 ~~
-                       [ s_0=0 ] ~~
-                       \{ s_0 \leftarrow 1\}
-                      }
-                      {\ostate{0}\xrightarrow{\delta}\ostate{0}}
-              }
-	\\
-      \inferrule
-        {
-          \inferrule
-              {0 \xrightarrow{acc(x)}_{C_2} 1}
-              {C_2
-                \models
-                \openrule
-                      {0 \xrightarrow{acc(x)}_{C_2} 1}
-                      {\ostate{0}\xrightarrow{acc(x)}\ostate{1}}
-              }
-        }
-        {
-          \textrm{acc(x);Q}\models
-              \openrule
-                  { 0 \xrightarrow {acc(x)}_{C_2} 1}
-                  {\ostate{0}\xrightarrow{acc(x)}\ostate{1}}
-        }   
-    }
-    {
-     \textrm{PN1}
-     \models
-        \openrule{
-                        0 \xrightarrow{\delta}_{C_1} 0, 0 \xrightarrow{acc(x)}_{C_2} 1 ~~
-                       \{\xrightarrow{hb_{12}}_P\} ~~ 
-                        [s_0=0 \!\land\! hb_{12}=\delta(x)] ~~ 
-                       \{s_0 \xleftarrow{} 1\}           
-                      }
-     {\ostate{00} \xrightarrow{\tau} \ostate{01}}
-      }\vspace{-4ex}
-\end{mathpar}
-  \caption{Proof of  $ot_{2}$ (interaction of process $P$ and action $acc(x)$) for ``P>>(acc(x);Q)''}
-  \label{usingrules:ot2}
-\end{figure}
-
-The proof tree uses TR1 twice, for the $\delta$ transition of $C_1$
-and for the $acc(x)$ transition of $C_2$, then uses an action
-$hb_{12}$ of hole $P$, and combines the results using the first vector
-of the PN2 sub-pNet, and the second vector of the top node according
-to TR2. This yields a final $\underline{\delta(x)}$ transition. The
-deduction tree in the figure shows how the predicates are generated in
-this process.
-
-\section{Generation of Open Automata}
-\label{section:implementation}
-In this section we describe the algorithm implementing the pNet
-semantics, the interaction with the Z3 SMT solver, and we show the
-result on our  example.
-
-Our algorithm starts with an open pNet, and builds its set of open
-transitions (OTs). Its main loop is a classical residual algorithm: starting
-from the initial global state, it pick a state in an unexplored set, and
-computes all possible OTs, adding their target states in the
-unexplored set, until this set is empty. As the potential set of
-global states is finite (see \cite{henrio:Forte2016}), this terminates.
-
-The inside loop (\emph{MakeTransitions} method) applies recursively
-the semantic rules following the structure of the pNet. 
-For pLTS at leaves, rule Tr1 simply take the pLTS transitions of the
-corresponding local state and build the predicate to generate the
-open transition. 
-On a pNet node to apply rule Tr2 we use two methods, combining and
-matching, to generate the new predicate of the open transitions in a
-hierarchical manner.
-
-Last, at the root of the pNet, the predicate of each OT is translated
-into SMTlib assertions, and checked for satifiability. Unsatisfiable
-OTs are pruned, and the final open automaton is computed as the set of
-global states reachable by satisfiable OTs.
-
-\begin{algorithm}
-\caption{Open Automaton Generation}
-\begin{algorithmic}[1]
-\Require The pNet node P.
-\State Initialize sets $U$, $E$ for unexplored/explored global states, $L$ for result OTs;
-\While{!isEmpty(U)}
-	\State Chose $S$ in $U$;
-	\State OT = MakeTransitions(P, S);
-        \State Store $OT$ in $L$; 
-	\For{each target global state $T$ from $OT \in L$}
-		\IfThen{$(!U.contains(T))\ \&\&\ (!E.contains(T))$}{Add $T$ into the $U$;}
-	\EndFor
-\EndWhile
-\State Prune the open transitions in $L$ using the SMT solver;
-\State \Return $L$;
-
-\end{algorithmic}  
-\end{algorithm}
-
-\begin{algorithm}
-\caption{MakeTransitions()}
-\begin{algorithmic}[1]
-\Require The pNet node P; The start global state S.
-\State Initialize a list $l$, $L$ for sub-transitions/transitions.
-	\For{each Subnet in P}
-	\\ ~~~ $\setminus \setminus$ Recursively applying Tr1 or Tr2 on the sub-nodes.
-                \State Store MakeTransitions(Subnet, S) in $l$;
-	\EndFor
-	\For{each $sv \in SV$}
-		\State $comb = Combining(l)$;
-                 \State $ot = Matching(sv, comb, hole, v)$;
-                 \State Store $ot$ in $L$; 
-	\EndFor
-\State \Return $L$;
-\end{algorithmic}  
-\end{algorithm}
-
-%
-%For holes, their behavior is unspecified, it doesn't have an exact
-%external presentation of action. We only give an action variable to each hole
-%and treat it as hole behavior to suppose working status of the
-%hole.
-%% Here should have a constraint that this variable belongs to the sort of hole.
-%In every case, the hole behaviors are unchanged, so we
-%only make the combinations of subnets' open transitions. 
-%
-
-\def\inactive{\{-\}}
-\paragraph{Combining:}
-The combining method enumerate all the possible behaviours of the
-subnets, as all the possible combinations of their open transitions.
-Assume that there is a collection of $n$ subnets $L = {s_1, s_2, ...,
-  s_n}$, if we notate $ot_i$ to be the set of open transitions of the
-subnet $s_i$ and ``$-$'' means the subnet is not involved.  
-Then the combination $\texttt{COMB}$, a set of n-tuples, is the
-cartesian product of sets :  
-\[\texttt{COMB} : (\inactive\cup ot_1) \times (\inactive\cup ot_2)\times ... \times (\inactive\cup ot_n) .\]
-
-%Algorithm 2 shows the combining algorithm for enumerating all possible
-%working status combinations from subnets. Dealing with a list $TR$
-%containing  sets of open transitions from different subnets,
-%the algorithm choses one of sets $L_{ot}$ and does combining on the
-%remaining part of $TR$ recursively. The case when a subnet is not working is
-%managed by adding a $null$ into the $L_{ot}$.
-
-\paragraph{Matching:}
-The next step, for each synchronisation vector, and each possible
-combination of behaviour of the subnets as generated by the \emph
-{Combining} method, consists in building the combined predicate,
-and the corresponding open transition.
-From a synchronization vector
-$sv_k\in SV = (a'_i)^{i\in I} (b'_j)^{j\in J}\rightarrow v'$
-and its guard $G_k$, a tuple of open transitions
-$C_n\in \texttt{COMB} = {(v_i)}^{i\in I}$, the hole behaviors $Hole$,
-and a fresh variable representing the result action $v$, we build the
-predicate:
-
-$$Matching(SV_k, C_n, Hole, v) = 
-\begin{array}{l}
-\forall {(a'_i)}^{i\in I},
-{(b'_j)}^{j\in J},v'.
-\\
-v_i=a'_i\land \, b_j=b'_j \land v=v' \land G_k
-\end{array}$$
-
-\paragraph{Filtering:}
-There may be several reasons why such a matching would fail:
-\begin{itemize}
-  \item if some subnet is marked as inactive in the vector, and the
-    chosen combinaison has an active behaviour at this position,
-  \item if some subnet action expression in the vector does not match (by
-    pattern-matching) the corresponding behaviour $C_n$,
-  \item or if the whole set of active subnet actions in the vector
-    cannot be matched (by unification) with the set $\{C_n\}$.
-\end {itemize}
-
-Each of these possible failures is more precise than the previous
-ones. But even when unification succeeds, it is still possible that
-the resulting predicate would be unsatisfiable, because of some
-incompatibility involving the guards. In our algorithm, we choose to
-apply only the simplest filter inside the \emph{Matching} method. All
-the rest will be checked later, using the satisfiability ckeck in the
-SMT engine.
-
-\subsection{Management of state variable assignments}
-%The pLTS contains some variables in each of its states (state
-%variables), or just as global states of the pLTS (global variables).
-%Both can be assigned in the pLTS transitions.
-%The algorithm composing assignments from subnets is different from the
-%generation of predicates. 
-%%When applying Tr1, we just keep the
-%%assignments in the Post of the open transition. And when it comes to
-%%Tr2, Post is the union of the assignments propagate from the
-%%subnets. 
-%The assignments provide value of the variables in
-%predicates. There is usually not only one assignment for a state variable as
-%several incoming transitions of a state can perform different
-%assignments on the same variable. The values of the
-%variables are necessary for checking satisfiability of the open
-%transitions together with predicates, miss of them may drop the
-%unsatisfiable results. In order to avoid such mistakes, the algorithm
-%manages the variables together with a list.
-%
-%The list we used contains triples $<v,\ S, \ AssignRH>$ set for each pLTS to record
-%the information of both state and global variables of the pLTS where $v$ is the variable in pLTS, $S$ is its owner state and $AssignRH$ is a list of expressions over other variables in the right hand side of assignments of $v$.
-The $S$ can be $null$ in the record triple, it means the variable is global in the pLTS belonging to all the states.
-%%So it should be noted that the changing of the value of the global state variable every time a transition is conducted.
-$AssignRH$ is the collection of all the possible expressions coming from the the right hand side of assignments.
-It keeps the information of the assignments for each variable.
-%We update the list of record triples every time Tr1 is applied, adding the right side of the assignments into corresponding expression lists.
-So the list keeps the all the assignments in the pLTS.
-Then we can track all the possible value of the variables when computing open transitions.
-%The initial value of the state variable is also seen as an assignment
-%for that variable. We must give a initial value to the global state
-%variable or there will be some problem in the start state. However, we
-%sometimes don't give initial values to the state variables (except the
-%global variables) as their initial values are decided by their first
-%assignments. Checking whether each variable is initialized before
-%being used is a separated problem, that should be done before starting
-%our algorithm.
-
-In a pLTS, there may be several incoming transitions of some states
-that assign potentially different values to a state variable.
-To handle such cases, the algorithm manages the variables together
-with a list for each pLTS.
-The list we used contains several triples <$v$, $S$, $AssignRH$> 
-where $v$ is the variable in pLTS, $S$ is its owner state and
-$AssignRH$ is a list of expressions over other variables in the right
-hand side of assignments of $v$.
-As a pragmatic extension to the formal definition, we also manage
-``global variables'', defined in all states of the pLTS.
-
-%There are some assignment on the variables in each of states of the pLTS (state variables), or just as global states of it (global variables).
-There is usually not only one assignment for a state variable, miss of them may drop the unsatisfiable results.
-In order to avoid such mistakes,
-
-%% \QIN{
-%% The list we used contains several triples <$v$, $S$, $AssignRH$> to
-%% record the information of both state and global variables of the pLTS,
-%% where $v$ is the variable in pLTS, $S$ is its owner state and
-%% $AssignRH$ is a list of expressions over other variables in the right
-%% hand side of assignments of $v$. It means the variable is global in
-%% the pLTS belonging to all the states, if $S$ is $null$. We update the
-%% list of record triples every time Tr1 is applied. Then we can track
-%% all the possible (symbolic) value of the variables when computing open transitions.
-%% }
-
-\subsection{Pruning the unsatisfiable results}
-\label{section:pruning}
-%We have used a brute-force method to generate all the possible open
-%transitions in the open automaton. It obviously contains some of
-%unsatisfiability in the open transitions. In
-%Fig~\ref{schema:unsat-ot}, we display an unsatisfiable open transition
-%from the result of the CCS running example. It shows the case that the
-%top level transmits out the action from the PN2, formula $a.P$, as
-%this time only PN2 is working and C1 is performing action $a$ when
-%hole $P$ is also working. When matching this case against the second
-%synchronization 
-%vector of PN2, transmitting the behavior from hole $P$ to the higher
-%level, is used while it is obviously violate the guard of the
-%vector. So we can easily find the contradiction between the generated
-%predicate term $ra:152:1=l \!\land\! a=:ra:152:1$ and the guard
-%composed into the predicate $a \neq l$.
-
-\begin{figure}[h]
-%$\begin{array}{@{}r@{}l@{}}
-%%{s0---a-->s1},   {---:hb:15:2-->},   (:ra:15:2 = act:sva:1:3)/\(:ra:152:1 = l)/\(a = :ra:152:1)/\(l!= a)/\(:hb:15:2 = y:sva:15:2)/\(:ra:15:2 = y:sva:15:2)/\(y:sva:15:2 != l)/\(:ra:1:3 = act:sva:1:3)
-%    ot  = &\openrule{\{0 \xrightarrow{a} 1\}, ~~\{\xrightarrow{:hb:15:2}\}, ~~:ra:15:2=act:sva:1:3 \\
-%    \OTland:ra:152:1=l \OTland a=:ra:152:1 \OTland a \neq l \OTland :hb:15:2 = y:sva:15:2 \\
-%    \OTland :ra:15:2 = y:sva:15:2  \OTland y:sva:15:2 \neq l \OTland :ra:1:3 = act:sva:1:3}
-%    {\ostate{00} \xrightarrow{:ra:1:3} \ostate{10}}\\
-%  \end{array}$
-%\caption{One of the unsatisfiable open transitions in CCS running example}  \label{schema:unsat-ot}
-%\end{figure}
-
-%{s0---delta-->s0},   {---:hb_P:12:1-->},   (:ra:11:1=l)/\(delta=:ra:11:1)/\(var_s0=0)/\(:hb_P:12:1=a1:sva_SV0:1:1)/\(:ra:1:1=a1:sva_SV0:1:1)/\(a1:sva_SV0:1:1!=delta(x)),   {var_s0 := 1}
-$\begin{array}{@{}r@{}l@{}}
-    ot  = &\openrule{\{0 \xrightarrow{\delta} 0\}, ~~\{\xrightarrow{:hb:12:1}\}, ~~\OTvar{:ra:11:1}=l \OTland \delta=\OTvar{:ra:11:1} \OTland \OTvar{s0}=0 \\
-     \OTland \OTvar{:hb:12:1}=\OTvar{a1:sva:1:1} \OTland \OTvar{:ra:1:1}=\OTvar{a1:sva:1:1} \OTland \OTvar{a1:sva:1:1} \neq \delta(x), ~~\{\OTvar{s0} \leftarrow 1\}}
-    {\ostate{00} \xrightarrow{\OTvar{:ra:1:1}} \ostate{00}}\\
-  \end{array}$
-\caption{One of the unsatisfiable open transitions in LOTOS running example}  \label{schema:unsat-ot}
-\end{figure}
-
-We use a brute-force method to generate all the possible open
-transitions in the open automaton, using all possible combinations of
-synchronization vectors. Naturally this builds some transitions where
-the predicates express incompatible constraints. Even if having an
-unsatisfiable (symbolic) transition in the open automaton would not be incorrect,
-we want to check them for satisfiability, and reduce the number of
-transitions and states in the automaton.
-In Fig.~\ref{schema:unsat-ot}, we display an example of an
-unsatisfiable open transition 
-from the result of our example. It shows the case where
-the controller C1 wants to move the control from $P$ to $(acc(x);Q)$,
-conducting a $\delta$ transition. However, a synchronization
-vector is chosen that does not match with this action, and we can
-easily find the contradiction in the 
-generated predicate term ``$\OTvar{:ra:11:1}=l \!\OTland\! \delta=\OTvar{:ra:11:1}$''.
-
-Checking satisfiability requires some symbolic computation
-on the action expressions and the predicates, and this 
-may depend on the specific theory of the action algebra. 
-We use the SMT solver Z3 to check the predicate of the result open transitions, 
-it will return whether the predicate is satisfiable or not.
-The ``Modulo Theory'' part of SMT solvers is important here, so that
-the solver can use specific properties of each action algebra.
-
-\begin{figure}[t]
-  %  \centerline{\includegraphics[width=12cm]{XFIG/SMTLIB2}}
-    \centerline{\includegraphics[width=\linewidth]{XFIG/SMTLIB2}}
-  \caption{The input of the Z3 solver in SMT-LIB language and the output result}  \label{schema:smt-lib}
-\end{figure}
-
-%% \begin{figure}[t]
-%%   \centerline{\includegraphics[width=10cm]{XFIG/Interaction}}
-%%   \caption{The architecture of the interaction between pNet API and Z3}  \label{schema:interaction}
-%% \end{figure}
-
-\subsection{Translation to SMTlib}
-
-\TODO{Eric: Replace by (excerpts of) the formal version, from appendix, and reduce to less than one page}
-
-\paragraph{Presentation of algebra}
-
-As seen in section
-\ref{section:pnets}, the \emph{term algebra} used to express the
-action expressions and data parameters is left open in
-the pNet definition.
-
-So, for a given language, we now need to specify its data and action
-domains, giving them an abstract syntax (sorts, constructors, operators,
-and predicates). We call this a \emph{Presentation}.
-We also define a concrete syntax, that will be used for
-pretty-printing, but also for translating the presentation, and the
-predicates, into Z3 syntax (see the ``declare-datatypes'' statement in
-Fig~\ref{schema:smt-lib}).
-
-An algebra presentation contains:
-
-\begin{itemize}
-	\item Sorts: Constants sets of the algebra or types of the data
-          and actions (integer and boolean sort are implicitly
-          declared).  There \emph{must} be one sort for actions, and
-          eventually others for the types of data
-          parameters. In the LOTOS example, 
-          we have the $Action$ sort: $\OTvar{Action = } \{ l, \delta,
-          r, p, q, acc \} .$
-
-	\item Operators:
-          %Operators used to construct action expressions; they are
-          constructors and predicates for data and action sorts. For
-          instance, in our LOTOS example, we
-          have a generic action constructor ``$ACT$'', taking as
-          argument an action litteral and a data parameter, declared as:
-          $\OTvar{ACT:}\OTvar{< Action, Data >} \rightarrow \OTvar{Action.}$, 
-        \item Constants: The satisfiability solver need to know which
-          actions in the pLTS behaviors are constants (like the $l$, $\delta$, 
-          $r$ of the controllers in running example). 
-          For a given pNet system, the sort $Action$ will include all
-          these constants.
-\end{itemize}
-
-\paragraph{Interaction with Z3}
-%\TODO{1. example input of Z3 in SMT-LIB.[DONE] 2. software architecture.[DONE]}
-%There are several ways to interact with the Z3 solver. 
-%It is possible to use Z3 interactively using the SMT-LIB
-%(Python-based) language. 
-From inside our algorithm code, we submit satisfiability requests to
-Z3 using its JAVA API. Here for readability, we
-show the Z3 code using its SMT-LIB input language. As an
-example in
-Fig~\ref{schema:smt-lib}, we show the input for checking the
-transition of Fig.~\ref{schema:unsat-ot}. It contains the declaration
-of the LOTOS action algebra types 
-and constructors, then the declaration of variables, and finally the
-predicate to be checked, encoded as a set of assertions.
-%% Generally, some $datatypes$ are declared to input the sorts, while here
-%% we only declare one $datatypes$ named $Action$ to involve all the
-%% constant actions. Then we input the predicate of this open transition
-%% in two parts: the variables contained in the predicate are declared
-%% first, then the terms of predicate are inputed as $assertions$ one by
-%% one. 
-The result "unsat" in the output is just what we expected.
-
-%\TODO{edit the figure to make it smaller in height [DONE]}
-
-%We present the architecture of the interaction with Z3 in
-%Fig~\ref{schema:interaction}.
-%For each OT generated at the toplevel of a pNet, the predicate must be
-%submitted for satisfiability check to Z3. For that we need to
-%translate into Z3 (Java-API) syntax, both the elements of the action
-%algebra, and the predicates itself, including the encoding of the
-%variable assignments (the Post part).
-%
-%The $presentation$ of the action algebra
-%is declared at the beginning of the algorithm as the $sorts$ and the
-%$operators$ will be used throughout the whole algorithm. It is
-%translated into $datatypes$ and $functions$ then submitted to the Z3
-%at the same time. Each candidate predicate will then be translated
-%into $assertions$ before submitted to Z3 after the algorithm
-%computing out all the possible open transitions, they act as
-%intermediate results there. Together with the $datatypes$ and
-%$functions$, the $assertions$ are used to check the satisfiability of
-%the predicate in Z3.
-
-To build the input submitted to Z3 for each OT,
-we translate the algebra $presentation$, the predicates and the
-variable assignments (the Post part) into Z3 (Java-API) syntax.
-% The $presentation$ and the predicates are translated separately.
-
-\paragraph{Translation of Action algebra presentation}
-\TODO{Exerpt of the formalisation}
-The $datatypes$ are declared according to the $sorts$ the users
-declared in the $presentation$. If the return type of the $functions$
-is one of the $datatypes$, we add this $function$ to the $datatypes$ declaration.
-So when we declare the operator ACT we illustrated in section 4.1, it
-will be just declared together with the constants like :\\
-\centerline{$\OTvar{(ACT\ (action3\ Action)(data\ Int))}$}
-
-The $functions$ can also be declared independently, it usually applies to functions returning integer or boolean, in the format like:\\
-\centerline{$\OTvar{(declare\text{-}fun\ MAX\ (Int\ Int)\ Int)}$}
-
-%Although in Fig~\ref{schema:smt-lib} we have not declared $functions$ outside of $datatypes$, there still exists $functions$ declared independently.
-The input and output types of the $function$ are also determined by the construct of the  $operators$ in the presentation.
-For example, we define a new operator to present the equation between two actions in LOTOS example $\text{EQUAL}$ in the format likes:
-%
-%\[EQUAL: \quad < Action , Action > \rightarrow Bool .\]
-%
-%It will be translated into the Z3 statement: 
-%
-%\[\text{(declare-fun\ EQUAL\ (Action\ Action)\ Bool) .}\]
-
-\paragraph{Translating assignments into predicate terms}
-\TODO{Exerpt of the formalisation}
-
-%The assignments are also taken into account when checking the
-%satisfiability of the open transitions as they represent the value of
-%the variables involved in an OT. In order to do that, we employs a
-%translation from assignments into term of predicates. The assignments
-%required to be translated are only those belong to the variables
-%contain in the start states of the open transitions. The assignments
-%are represented as equations between the variables and the expressions
-%on the right side of assignment. For the assignments of the same
-%variable, we do not figure out which state is the precursor of current
-%state, we keep all these possible equations instead, and generate the
-%disjunction of these equations. The state could always move to the
-%target state if there exists one of the values of its variable
-%satisfies the guard.
-%%\TODO{It won't matter the variable of the next state
-%%except that the right hand side expression contain its variables. This
-%%is a problem left to be solved in our future work. WHICH PROBLEM ?}
-%After that, for the assignments of the different variables, we generate a conjunction of them. This way we obtain a new term of the predicate involving assignments of the variables.
-
-State-variable assignments are also treated as a part of the
-predicates when checking the satisfiability. % Here we need conduct some
-% translations,
-For each assignement in a $\Post$ predicate, such as $\{s_0 \leftarrow 1\}$ in section
-~\ref{section:op-semantics}, we translate it into an equation
-$s_0=1$. For several assignments of the same variable in the same state,
-we generate the disjunction of 
-these equations. Correspondingly, we generate a conjunction for the
-assignments from different variables.
-
-\paragraph{Checking satisfiability}
-
-% We check the satisfiability of open transitions on the top level of
-% the pNet, treating these open transitions as the intermediate result
-% of the algorithm. After we get the intermediate results of open
-% transitions, we check them one by one.
-Here we declare first all the variables in the predicates, with their
-sorts.
-An example of syntax is::\\
-\centerline{$\OTvar{(declare-const\ |:ra:1:1|\ Action)}$}
-
-\noindent Then each term of the
-predicate is an assertion in Z3, as an example, in the former
-unsatisfiable result in Fig~\ref{schema:unsat-ot}, the contradiction is occurred in terms: \\
-\centerline{$\OTvar{(:ra:11:1=l)} \OTland \OTvar{(delta=:ra:11:1)}$}\\
-from which we generate the following two assertions:\\
-\centerline{$\OTvar{(assert\ (=\ |:ra:11:1|\ l))\ \ \ (assert\ (=\ delta\ |:ra:11:1|))}$}
-
-\noindent The predicate submitted to the Z3 also contains the
-assignments encodings.
-In the case of $ot_2$, it
-gives the assertion:\\
-\centerline{$\OTvar{assert (or (= var\_s0 0) (= var\_s0 01)))}$}
-
-\subsection{Simplification of Predicates}
-\ERIC{: motivated, add refs, and an abstract presentation of stuff from pages 19-20}
-
-\subsection{Result of the running example}
-\label{section:full-result}
-
-\TODO{Xudong: Update: we have 11 satisfiable OTs here}
-Our tool builds 30 open
-transitions, out of which 27 are detected unsatisfiable by Z3, we
-get only 3 results left; the resulting open automaton is shown in
-Fig. ~\ref{schema:lotos-result}, together with its open transitions.
-
-The resulting open transitions represent all the
-possible movements of the LOTOS example.
-What can be observed is any actions of the process $P$ from the beginning, until $P$ performs a $\delta(x)$ and the value of
-$x$ is transmitted to the $acc(x);Q$ giving out a silent action. Such behavior is performed by the $ot_1$ then $ot_2$. 
-Then it keeps presenting the behavior of $Q$, as seen in $ot_3$. 
-%The $ot_1$ transition means that the actions of the process $P$ could
-%be transmitted out, until $P$ performs a $\delta(x)$ and the value of
-%$x$ is transmitted, through transition
-%$ot_2$. The other 3 open transitions shows the behaviors of the
-%process $Q$ while the $ot_3$ and $ot_4$ won't be performed as the
-%controller has already set the value $s_0$ to 1 in the previous
-%action.
-
-\begin{figure}[t]
-   \centerline{\includegraphics[width=12cm]{XFIG/BIPresult-ArchFailureTimerMax}}
-   \caption{Open Automaton\TODO{syntax could be better...}}  \label{schema:resultOA}
- \end{figure}
-
-\begin{figure}[h]
-%  \centerline{\includegraphics[width=5cm]{XFIG/LOTOSresult}}
-  \TODO{Detaisl of some OTs of the FailureTimer}
-
-$\begin{array}{@{}r@{}l@{}}
-    ot_1  = &\openrule{\{0 \xrightarrow{l}_{C_1} 0\}, ~~\{\xrightarrow{hb_{1}}_P\}, ~~[s_0=0 \!\land\! hb_{1} \neq \delta(x) \!\land\! v_1=hb_{1}]}
-    {\ostate{00} \xrightarrow{v_1} \ostate{00}}\\
-  \end{array}$
-
-$\begin{array}{@{}r@{}l@{}}
-    ot_2  = &\openrule{\{0 \xrightarrow{\delta}_{C_1} 0, 0 \xrightarrow{acc(x)}_{C_2} 1\}, ~~\{\xrightarrow{hb_{2}}_P\}, ~~[s_0=0 \!\land\!
-hb_{2}=\delta(x) \!\land\!
-v_2=\underline{\delta(x)}], ~~\{s_0 \xleftarrow{} 1\}}
-    {\ostate{00} \xrightarrow{v_2} \ostate{01}}\\
-  \end{array}$
-
-\caption{The open automaton of the LOTOS formula}  \label{schema:lotos-result}
-\end{figure}
-
-%\subsubsection{Result of CCS example}
-%\QIN{
-%also can present all the possible behavior of that CCS formula with 16 open
-%transitions in Fig. ~\ref{schema:ccs-result}, here we omitted the details of open transitions. 
-%In this example, there are 32 more transitions detected unsatisfiable by Z3.
-%}
-%
-%\QIN{
-%Here we only show one of the result transitions. It presents the value-passing between $a.P$ and $b.Q$ and they are synchronized then
-%give out an silent action $\tau$, process $P$ and $Q$ should not work in this case.
-%}
-%
-%\begin{figure}[h]
-%  \centerline{\includegraphics[width=5cm]{XFIG/CCSresult}}
-%  
-%  $\begin{array}{@{}r@{}l@{}}
-%    ot_1  = &\openrule{\{0 \xrightarrow{a}_{C_1} 1, 0 \xrightarrow{b}_{C_2} 1\}, ~~a=!ch_{11}(v_{11}) \!\land\! b=?ch_{11}(v_{11}) \!\land\! a\neq l \!\land\! b\neq r\!\land\! v_1=\tau}
-%    {\ostate{00} \xrightarrow{v_1} \ostate{11}}\\
-%  \end{array}$
-%  
-%\caption{The open automaton of the CCS parallel formula}  \label{schema:ccs-result}
-%\end{figure}
-
-%% \QIN{
-%% To sum up, from the pNets encoding the formulas of given algebra, which inputed by the user, we can exactly construct
-%% the open automaton for them. 
-%% }
-
-\section{Conclusion and Discussion}
-\label{section:conclusion}
-
-In this paper we presented the algorithm for generating an open
-automaton representing the semantics of an open pNet, and we described
-the implementation of the
-algorithm. Our implementation includes two main parts. First, we
-compute all the possible open transitions. The actions in pLTS and
-hole behaviors are composed in the algorithm while the generation of
-predicate need to match the combinations of the subnets with the
-synchronization vectors. Some of the open transitions obtained at this
-intermediate step, constructed in a structural manner from all
-possible combinations of possible logical predicates, may
-contain predicates which do not represent any possible concrete
-instantiations. 
-To get rid of these useless transitions, we use the SMT solver Z3 for checking the
-satisfiability of the predicate in each open transition. In
-order to do that, we encode into Z3 the action algebra presentation,
-the a representation of the predicates, before submitting them to the
-Z3 solver. We implemented our algorithm in the VerCors platform and use some
-running examples, encoding expressions from various process algebras, to test the
-algorithm. Our use-cases show that our encoding
-identifies successfully all unsatisfiable open transitions and that
-the resulting automaton reflects correctly the expected 
-movements of the encoded process expressions.
-
-Among the questions arising during this work, an important one is the
-efficiency of Z3 for our needs. Z3 is famous for being very fast for
-solving very large sets of assertions, and this could be important for
-us. But we encountered  some problems during the implementation the
-checking method using Z3. For example, if the $functions$ and the
-$datatypes$ part of the algebra presentation we submit to the solver
-are independent with each other, then checking the $assertions$ is a
-simple work. However, $functions$ on recursive $datatypes$ make it
-more complex, some special rules might be defined by user for the
-induction. Also, we need more evidence that dealing with more complex
-action algebras, that would involve axiomatizing their data structures
-into Z3 theories, will indeed allow us to decide validity of
-predicates.
-We may also try other automatic theorem provers, depending on the structure of the proofs we need.
-
-\TODO{Change perspective: we are working on the formal extensino of
-  BIB architectures, and their semantics in terms of pNets. Then
-  bisimulation and model-checking principles adapted to open pNet
-  systems are under development}
-
-Naturally, our next goals after the generation of the open automata
-will be to model-check, and to check equivalence of  pNets. While
-model-checking open automata (with a suitable logic including
-predicates on data) seems easy to define, equivalence checking is more challenging.
-In previous paper, we
-have already found the FH-bisimulation, inspired by~\cite{deSimone85} as a
-suitable definition. But usual approaches of bisimulation by partition
-refinement does not work easily with symbolic transitions. In a first
-step we may want instead to define and implement an algorithm for
-checking that a given equivalence relation between open automata 
-states is indeed a FH-Bisimulation. Finding automatically a
-bisimulation relation or the most general bisimulation will be more
-challenging. It appears also that when comparing different pNets with
-different structure, strong bisimulation will be too strong a notion,
-and that we will have to define proper notions of weak equivalence or
-refinements.
-
-Before that work, we need to reconsider the result open transitions
-from our algorithm. The ideal
-result that we showed in the bottom part of
-Fig.~\ref{schema:lotos-result} is not the one generated by the algorithm,
-because the original one contains many intermediate
-variables, such as fresh local variables of synchronization
-vectors, and fresh result variables of intermediate open transitions.
-Such intermediate variables come from the way predicates are
-generated, and depends on the particular structure of the pNet. But
-they are not significant in the resulting behavior, and should be
-eliminated before comparing such behavior with another pNet.
-To eliminate the intermediate variables in the predicate, we want to define
-the set of the significant variables that we won't eliminate: the
-local variables of pLTS transitions, the hole behaviors and the result
-action at the top level.
-The result of the elimination will be simpler predicates, that can be
-successfully compared (e.g. by Z3) within the bisimulation checking
-algorithm.
-
-\bibliographystyle{lncs/splncs}
-
-% \bibliography{oasis,biblio}
-\bibliography{biblio}
-
-% \newpage
-\appendix
-
 \section{More details on the generation algorithm}

### 2018-01-15 2017-Xudong-SMT/FM-2018-extended.tex
small bugs

@@
 open automaton semantics. This automaton may then be used to prove
-bahavioral properties, like e.g., \TODO{ par exemple ..}
+behavioral properties, like e.g., \TODO{ par exemple ..}
 
@@
 \item[$\bullet$] $S_j \subseteq \AlgA$ is a set of action terms,
-  denoting the $\Sort$\footnote{The formal definition of $Sorts$ (the
+  denoting the $\Sort$\footnote{The definition of $Sorts$ (the
     set of actions of a Hole  
@@
         }
-	{<s0,t0> \xrightarrow {v} <s1,t1>}
+	{\ostate{s0,t0} \xrightarrow {v} \ostate{s1,t1}}
 	\end{mathpar}

### 2018-01-16 2017-Xudong-SMT/FM-2018-extended.tex
OA fig

@@
 $\begin{array}{r@{}l}
-    ot  = &\openrule{\{0 \xrightarrow{\OTvar{resume(false)}} 0, 0 \xrightarrow{\OTvar{start(true)}} 1\}, ~~\{\xrightarrow{hb}\},~~\OTvar{resume(false)}=\OTvar{failure(}\OTvar{b}_1\OTvar{)}\\
+    ot  = &\openrule{\{0 \xrightarrow{\OTvar{resume(false)}} 0, 0 \xrightarrow{\OTvar{start(true)}} 1\}, ~~\{\xrightarrow{hb}\},~~\OTvar{resume(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
     			     \OTland \OTvar{start(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)} \OTland \OTvar{hb}=\OTvar{fail(}\OTvar{b}_0\OTvar{)} \OTland \OTvar{v}=\OTvar{\underline{fail}}\\
@@
 
-The resulting open transitions represent all the
-possible movements of the LOTOS example.
-What can be observed is any actions of the process $P$ from the beginning, until $P$ performs a $\delta(x)$ and the value of
-$x$ is transmitted to the $acc(x);Q$ giving out a silent action. Such behavior is performed by the $ot_1$ then $ot_2$. 
-Then it keeps presenting the behavior of $Q$, as seen in $ot_3$. 
-%The $ot_1$ transition means that the actions of the process $P$ could
-%be transmitted out, until $P$ performs a $\delta(x)$ and the value of
-%$x$ is transmitted, through transition
-%$ot_2$. The other 3 open transitions shows the behaviors of the
-%process $Q$ while the $ot_3$ and $ot_4$ won't be performed as the
-%controller has already set the value $s_0$ to 1 in the previous
-%action.
+To improve the readability of this figure, we used the following conventions:
+we omit the transitions of the two pLTS, and the set of ``working''
+holes; and we directly write the resulting action as first element of
+each OT, rather than including it as an equality inside the
+predicate. 
+\TODO{missing some comments on this result OA}.
 
 \begin{figure}[t]
-   \centerline{\includegraphics[width=12cm]{XFIG/BIPresult-ArchFailureTimerMax}}
-   \caption{Open Automaton\TODO{syntax could be better...}}  \label{schema:resultOA}
+   \centerline{\includegraphics[width=12cm]{XFIG/FailureTimerOA}}
+   \caption{Open Automaton}  \label{schema:resultOA}
  \end{figure}
@@
 
-\TODO{Change perspective: we are working on the formal extensino of
+\TODO{Change perspective: we are working on the formal extension of
   BIB architectures, and their semantics in terms of pNets. Then
@@
 
-\bibliographystyle{lncs/splncs}
-
-% \bibliography{oasis,biblio}
-\bibliography{biblio}
-
 % \newpage
@@
 \begin{lstlisting}[basicstyle=\scriptsize\ttfamily, frame=single]
-   {s0---failure(true)-->s1, t0---start(true)-->t1}, {---:hb_B:13:1-->},
-   (failure(true)=failure(b1:sva_SV0:1:1))/\(start(true)=start(b2:sva_SV0:1:1))
+   {s0---fail(true)-->s1, t0---start(true)-->t1}, {---:hb_B:13:1-->},
+   (fail(true)=fail(b1:sva_SV0:1:1))/\(start(true)=start(b2:sva_SV0:1:1))
    /\(:hb_B:13:1=fail(b0:sva_SV0:1:1))/\((b1:sva_SV0:1:1=b2:sva_SV0:1:1)
@@
 
-   {s1---failure(false)-->s1, t1---start(false)-->t1},   {---:hb_B:13:1-->},
-   (failure(false)=failure(b1:sva_SV0:1:1))/\(start(false)=start(b2:sva_SV0:1:1))
+   {s1---fail(false)-->s1, t1---start(false)-->t1},   {---:hb_B:13:1-->},
+   (fail(false)=fail(b1:sva_SV0:1:1))/\(start(false)=start(b2:sva_SV0:1:1))
    /\(:hb_B:13:1=fail(b0:sva_SV0:1:1))/\((b1:sva_SV0:1:1=b2:sva_SV0:1:1)

### 2018-01-16 2017-Xudong-SMT/FM-2018-extended.tex
Moved the BIPspec figure back into XFIG Added corresponding LaTeX macros to figtex2eps-preamble.tex Some clean-up in .gitignore (to avoid updating the index after every run of 'make pdf' Some minor editing in the Introduction

@@
 
+\usepackage{hyperref}
 \usepackage{macrospNets}
@@
         \and Shanghai Key Laboratory of Trustworthy Computing, ECNU, China
-\and INRIA Lille }
+\and INRIA Lille -- Nord Europe, 40 avenue Halley,
+59650 Villeneuve d'Ascq
+France}
 \date{}                                           % Activate to display a given date or no date
@@
   \item \ERIC{We show the interest of this approach on an
-    industrial-inspired use-case, namely one architectural pattern
-    extracted from the BIP specification of a nano satellite on-bord
+    industry-inspired case-study, namely one architectural pattern
+    extracted from the BIP specification of a nanosatellite on-board
     software.} 
@@
 already integrated several provers, like Z3, as modules for proving
-the proof obligations generated from the model inputed by user. 
+the proof obligations generated from the model provided by the user. 
 The prover we used, which also happens to be Z3, is developed by Microsoft Research
@@
 denote classically $\overline{a}$ a family when the indexing set is
-not meaningful.  $\uplus$ is the disjoint union on
+irrelevant.  $\uplus$ is the disjoint union on
 indexed sets.

### 2018-01-16 2017-Xudong-SMT/FM-2018-extended.tex
New version of the BIP diagramme for the Failure Monitor architecture -- consumes less space on the page Yet more cleanup in the .gitignore file
up to page 11

@@
 
-%% This paper presents our open automaton computing algorithm and its
-%% implementation using the pNet API from the VerCors platform.
-%% Comparing
-%% the result of the algorithm with 
-%% the manual result on our running examples shows that the algorithm
-%% works properly in computing the pNet semantics.
-%% The
-%% algorithm contains the method computing the open transitions composing
-%% the transitions from the subnets according to several defined rules
-%% the open transitions need to satisfy. These results are not the final
-%% results in fact, because they contain some unsatisfiable results we need
-%% to eliminate. To eliminate those unsatisfiability, we interact with an
-%% automatic theorem prover for satisfiability checking.
-
 \paragraph{Contribution}
@@
   model, including management of variables and assignments.
-%  \item We extended the meta-model of action expressions, and the
-%    associated API, in the VerCors platform, to be able to manage
-%    parameterisation over the action algebra operators.
 \item We implement the interaction between our algorithm and the Z3
@@
     generated by the algorithm.
-  \item \ERIC{We show the interest of this approach on an
+\item We show the interest of this approach on an
     industry-inspired case-study, namely one architectural pattern
     extracted from the BIP specification of a nanosatellite on-board
-    software.} 
+    software.
 \end{itemize}
@@
 Coq~\cite{armand:CPP2011},
-%Coq~\cite{armand:CPP2011,besson:CPP2011},
 Isabelle~\cite{blanchette:FroCoS2011} or others.
@@
 of pNet, including its structural rules.
-%, and a sketch of the algorithm
-%to compute such semantics, but also explains the enhancement we have
-%done to these definitions
 Section \ref{section:implementation} explains in details our
@@
 $a_i^{i\in I}$
-%, or equivalently  $(i\mapsto a_i)^{i\in I}$
 denotes a family of elements $a_i$ indexed over the
-set $I$. % Such a family
-% is equivalent to the mapping $(i\mapsto a_i)^{i\in I}$.
-% To specify the set over which the structure is indexed,
-% indexed structures are always denoted with an exponent of the form $i\in I$
-% (arithmetic only appears in the indexes if necessary).
-$a_i^{i\in I}$ defines both $I$ the set over which the family is
-indexed (called \emph{range}), and $a_i$ the elements of the family.
-E.g., $a^{i\in\{3\}}$ is the mapping with a single entry $a$ at index
-$3$ ; abbreviated $(3\mapsto a)$ in the following.
+set $I$.
 When this is not
@@
 denote classically $\overline{a}$ a family when the indexing set is
-irrelevant.  $\uplus$ is the disjoint union on
-indexed sets.
-
-\TODO{Eric: merge term algebra, algebra pres, and add a short example (BIP)}
+irrelevant.  $\uplus$ is the disjoint union on indexed sets.
 
@@
 Our models rely on a notion of parameterized actions, that are
-symbolic expressions using data types and variables. As our model aims
-at encoding the low-level behavior of possibly very different
+symbolic expressions using data types and variables. As we want to encode
+the low-level behavior of possibly very different
 programming languages, we do not want to impose one specific algebra
@@
 communications.
-\QIN{
-\paragraph*{Algebra presentations}
+
+\paragraph*{Algebra presentations.}
+In practice, the parameterization of the pNet model by some specific
+action is realized through the definition of an ``algebra
+presentation''. It will be used to define formaly a notion of
+well-formness of a pNet system, and the translation of the pNet
+semantics into the SMT engine input language.
+
 \begin{definition}
@@
 \end{definition}
-}
 
@@
    \centerline{\includegraphics[width=12cm]{XFIG/FailureTimerPNET}}
-   \caption{FailureTimer pNet encoding}  \label{schema:BIParchitecture}
+   \caption{FailureTimer pNet encoding\TODO{on peut gagner un peu en hauteur}}  \label{schema:BIParchitecture}
  \end{figure}
@@
 
-The semantics of open pNets will be defined as an open automaton,that
+The semantics of open pNets will be defined as an open automaton, that
 is an automaton where each transition composes transitions 
@@
 actions of some holes; the transition occurs if some predicates hold,
-and can involve a set of state modifications.
+and can involve a set of state modifications. Each state of an open
+automaton has a set of \emph{state variables} that can be assigned
+incoming transitions.
 
@@
 \paragraph{Structural Semantic Rules:}
-\TODO{I have pushed the rules in the appendix, we need to add a short high
-  level desciption here.}
-
-\TODO{ERIC: I choose here to remove the expample of construction of an
-  OT as a deduction tree. First because it was already published in
-  the Forte'16 paper, but also because it is not the way the algorithm
-  is working.}
-
-%% \begin{example} \emph{Using the operational rules to compute  open-transitions: }
-%%   in Fig. \ref{usingrules:ot2} we show the deduction tree used to construct and prove the 
-%%   open transition $ot_2$.
-%% \end{example}
-
-%% \begin{figure}[h]
-%% %  \vspace{-10mm}
-
-%% \begin{mathpar}
-%%   \small
-%%   \inferrule
-%%     {
-%%           \inferrule
-%%               {0 \xrightarrow {\delta}_{C_1} 0 ~~
-%%                [ s_0=0 ]
-%%               }
-%%               {C_1
-%%                 \models
-%%                 \openrule
-%%                       {0 \xrightarrow{\delta}_{C_1} 0 ~~
-%%                        [ s_0=0 ] ~~
-%%                        \{ s_0 \leftarrow 1\}
-%%                       }
-%%                       {\ostate{0}\xrightarrow{\delta}\ostate{0}}
-%%               }
-%% 	\\
-%%       \inferrule
-%%         {
-%%           \inferrule
-%%               {0 \xrightarrow{acc(x)}_{C_2} 1}
-%%               {C_2
-%%                 \models
-%%                 \openrule
-%%                       {0 \xrightarrow{acc(x)}_{C_2} 1}
-%%                       {\ostate{0}\xrightarrow{acc(x)}\ostate{1}}
-%%               }
-%%         }
-%%         {
-%%           \textrm{acc(x);Q}\models
-%%               \openrule
-%%                   { 0 \xrightarrow {acc(x)}_{C_2} 1}
-%%                   {\ostate{0}\xrightarrow{acc(x)}\ostate{1}}
-%%         }   
-%%     }
-%%     {
-%%      \textrm{PN1}
-%%      \models
-%%         \openrule{
-%%                         0 \xrightarrow{\delta}_{C_1} 0, 0 \xrightarrow{acc(x)}_{C_2} 1 ~~
-%%                        \{\xrightarrow{hb_{12}}_P\} ~~ 
-%%                         [s_0=0 \!\land\! hb_{12}=\delta(x)] ~~ 
-%%                        \{s_0 \xleftarrow{} 1\}           
-%%                       }
-%%      {\ostate{00} \xrightarrow{\tau} \ostate{01}}
-%%       }\vspace{-4ex}
-%% \end{mathpar}
-%%   \caption{Proof of  $ot_{2}$ (interaction of process $P$ and action $acc(x)$) for ``P>>(acc(x);Q)''}
-%%   \label{usingrules:ot2}
-%% \end{figure}
-
-%% The proof tree uses TR1 twice, for the $\delta$ transition of $C_1$
-%% and for the $acc(x)$ transition of $C_2$, then uses an action
-%% $hb_{12}$ of hole $P$, and combines the results using the first vector
-%% of the PN2 sub-pNet, and the second vector of the top node according
-%% to TR2. This yields a final $\underline{\delta(x)}$ transition. The
-%% deduction tree in the figure shows how the predicates are generated in
-%% this process.
+The semantics of pNet in term of open automata has been defined in
+\cite{henrio:Forte2016}. For convenience we include these 
+rules in Appendix \ref{appendix:semRules}.
 
@@
 
-The inside loop (\emph{MakeTransitions} method) applies recursively
-the semantic rules following the structure of the pNet. 
-For pLTS at leaves, rule Tr1 simply take the pLTS transitions of the
-corresponding local state and build the predicate to generate the
-open transition. 
-On a pNet node to apply rule Tr2 we use two methods, combining and
-matching, to generate the new predicate of the open transitions in a
-hierarchical manner.
-
-Last, at the root of the pNet, the predicate of each OT is translated
-into SMTlib assertions, and checked for satifiability. Unsatisfiable
-OTs are pruned, and the final open automaton is computed as the set of
-global states reachable by satisfiable OTs.
-
-\begin{algorithm}
+\begin{algorithm}[h]
 \caption{Open Automaton Generation}
@@
 \end{algorithm}
+
+The inside loop (\emph{MakeTransitions} method) applies recursively
+the semantic rules following the structure of the pNet. 
+For pLTS at leaves, rule Tr1 simply take the pLTS transitions of the
+corresponding local state and build the predicate to generate the
+open transition. 
+On a pNet node to apply rule Tr2 we use two methods, combining and
+matching, to generate the new predicate of the open transitions in a
+hierarchical manner.
+
+Last, at the root of the pNet, the predicate of each OT is translated
+into SMTlib assertions, and checked for satifiability. Unsatisfiable
+OTs are pruned, and the final open automaton is computed as the set of
+global states reachable by satisfiable OTs.
 
@@
 
-In a pLTS, there may be several incoming transitions of some states
+In a pLTS, there may be several incoming transitions 
 that assign potentially different values to a state variable.
-To handle such cases, the algorithm manages the variables together
-with a list for each pLTS.
-The list we used contains several triples <$v$, $S$, $AssignRH$> 
+To handle such cases, the algorithm manages the assignments
+within a list for each pLTS.
+The list we used contains triples <$v$, $S$, $AssignRH$> 
 where $v$ is the variable in pLTS, $S$ is its owner state and
@@
 hand side of assignments of $v$.
-As a pragmatic extension to the formal definition, we also manage
-``global variables'', defined in all states of the pLTS.
+% As a pragmatic extension to the formal definition, we also manage
+% ``global variables'', defined in all states of the pLTS.
+For a global state in the open automaton, getting the set of state
+variables (which may be used in a transition) will simply be the union
+of state variables of the individual pLTS states constituting this
+global state (variables of different pLTS are distinct). We define:
+\begin{itemize}
+  \item $SVars(gs)$ the state variables of all states in the global
+    state $gs$
+  \item $Assigns(svar)$ the set of possible assignments of variable
+      $svar$.
+\end{itemize}
 
@@
 
-We use a brute-force method to generate all the possible open
-transitions in the open automaton, using all possible combinations of
-synchronization vectors. Naturally this builds some transitions where
+Our matching/filtering strategy builds some transitions where
 the predicates express incompatible constraints. Even if having an
@@
 transitions and states in the automaton.
-\TODO{Change...} In Fig.~\ref{schema:unsat-ot}, we display an example of an
+In Fig.~\ref{schema:unsat-ot}, we display an example of an
 unsatisfiable open transition 
 from the result of our example. It shows the case where
-the controller C1 wants to move the control from $P$ to $(acc(x);Q)$,
-conducting a $\delta$ transition. However, a synchronization
-vector is chosen that does not match with this action, and we can
-easily find the contradiction in the 
-generated predicate term ``$\OTvar{:ra:11:1}=l \!\OTland\! \delta=\OTvar{:ra:11:1}$''.
+the failure controller performs a ``$resume$'' action, while the timer
+executes a ``$start$''. The chosen synchronization
+vector does not match with these actions,as appears in the predicate
+fragment ``$\OTvar{resume(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}$''.
+Fig.~\ref{schema:smt-lib} shows the translation of this OT predicate
+in the SMTlib syntax. Here we display also the proof generated by Z3,
+though in practice our tool only needs the brute information ``sat'' or ``unsat''.
 
@@
 
-As seen in section
-\ref{section:pnets}, the \emph{term algebra} used to express the
-action expressions and data parameters is left open in
-the pNet definition.
-
-So, for a given language, we now need to specify its data and action
-domains, giving them an abstract syntax (sorts, constructors, operators,
-and predicates). We call this a \emph{Presentation}.
-We also define a concrete syntax, that will be used for
-pretty-printing, but also for translating the presentation, and the
-predicates, into Z3 syntax (see the ``declare-datatypes'' statement in
-Fig~\ref{schema:smt-lib}).
-
-An algebra presentation contains:
-
-\begin{itemize}
-	\item Sorts: Constants sets of the algebra or types of the data
-          and actions (integer and boolean sort are implicitly
-          declared).  There \emph{must} be one sort for actions, and
-          eventually others for the types of data
-          parameters. In the LOTOS example, 
-          we have the $Action$ sort: $\OTvar{Action = } \{ l, \delta,
-          r, p, q, acc \} .$
-
-	\item Operators:
-          %Operators used to construct action expressions; they are
-          constructors and predicates for data and action sorts. For
-          instance, in our LOTOS example, we
-          have a generic action constructor ``$ACT$'', taking as
-          argument an action litteral and a data parameter, declared as:
-          $\OTvar{ACT:}\OTvar{< Action, Data >} \rightarrow \OTvar{Action.}$, 
-        \item Constants: The satisfiability solver need to know which
-          actions in the pLTS behaviors are constants (like the $l$, $\delta$, 
-          $r$ of the controllers in running example). 
-          For a given pNet system, the sort $Action$ will include all
-          these constants.
-\end{itemize}
+%% As seen in section
+%% \ref{section:pnets}, the \emph{term algebra} used to express the
+%% action expressions and data parameters is left open in
+%% the pNet definition.
+
+%% So, for a given language, we now need to specify its data and action
+%% domains, giving them an abstract syntax (sorts, constructors, operators,
+%% and predicates). We call this a \emph{Presentation}.
+%% We also define a concrete syntax, that will be used for
+%% pretty-printing, but also for translating the presentation, and the
+%% predicates, into Z3 syntax (see the ``declare-datatypes'' statement in
+%% Fig~\ref{schema:smt-lib}).
+
+%% An algebra presentation contains:
+
+%% \begin{itemize}
+%% 	\item Sorts: Constants sets of the algebra or types of the data
+%%           and actions (integer and boolean sort are implicitly
+%%           declared).  There \emph{must} be one sort for actions, and
+%%           eventually others for the types of data
+%%           parameters. In the LOTOS example, 
+%%           we have the $Action$ sort: $\OTvar{Action = } \{ l, \delta,
+%%           r, p, q, acc \} .$
+
+%% 	\item Operators:
+%%           %Operators used to construct action expressions; they are
+%%           constructors and predicates for data and action sorts. For
+%%           instance, in our LOTOS example, we
+%%           have a generic action constructor ``$ACT$'', taking as
+%%           argument an action litteral and a data parameter, declared as:
+%%           $\OTvar{ACT:}\OTvar{< Action, Data >} \rightarrow \OTvar{Action.}$, 
+%%         \item Constants: The satisfiability solver need to know which
+%%           actions in the pLTS behaviors are constants (like the $l$, $\delta$, 
+%%           $r$ of the controllers in running example). 
+%%           For a given pNet system, the sort $Action$ will include all
+%%           these constants.
+%% \end{itemize}
 
@@
 
-% \newpage
+\newpage
 \appendix
+\section{Appendix}
+The following appendices are included for the convenience of reviewers.
+Our intention is to publish as a research report, before final publication, an
+extended version containing all technical detials, proofs, and more examples.
 
 \section{pNet semantic rules}
+\label{appendix:semRules}
 
 \paragraph{Note:} For convenience, we have included here the semantic rules for pNets,
-that were already published in \cite{Forte}.
+that were already published in \cite{henrio:Forte2016}.
 
@@
 \section{More details on the generation algorithm}
-\subsection{Algebra specification}
-\subsection{Term algebra: type system and static semantics}
-Our models rely on a notion of parameterized actions, that are
-symbolic expressions using data types and variables. As our model aims
-at encoding the low-level behavior of possibly very different
-programming languages, we do not want to impose one specific algebra
-for denoting actions, nor any specific communication mechanism. So we
-leave unspecified the constructors of the algebra that will allow building
-expressions and actions. Moreover, we use a generic {\em action interaction}
-mechanism, based on unification between two or more action
-expressions. This will be used in the semantics of synchronization
-vectors to express various kinds of communication or synchronization mechanisms.
-
-\def\Talg{\mathcal{T}_{\Sigma,\P}}
-Formally, we assume the existence of a term algebra $\Talg$,
-where $\Sigma$ is the signature of the data and action constructors,
-and $\P$ a set of variables. Within $\Talg$, we distinguish a set of
-data expressions $\mathcal{E}_\P$, including a set of boolean
-expressions $\mathcal{B}_{\P}$ ($\mathcal{B}_{\P}\subseteq\mathcal{E}_\P$).
-On top of $\mathcal{E}_\P$ we build the action algebra
-$\mathcal{A}_\P$, with $\mathcal{A}_P\subseteq\mathcal{T}_\P,
-\mathcal{E}_P\cap\mathcal{A}_P=\emptyset$;
-naturally action terms will use data expressions as sub-terms.
-The function $\vars(t)$ identifies the set of variables in a term
-$t\in\AlgT$.
-
-pNets can encode naturally the notion of input actions as found e.g. in value-passing CCS
-\cite{Milner89} or of usual point-to-point message passing calculi, but it also allows
-for more general mechanisms, like gate negotiation in Lotos, or broadcast
-communications.
-
-\subsection{Fresh variables}
-
-%The variables in each synchronization vector are considered local, so
-%does the variables of an open transition such as its hole behaviors
-%and its result action. So we want rename the variables to make them
-%unique on every occurrence of a vector. Similarly, the name given to
-%the hole behaviors for each hole or the result action for each open
-%transition must be distinct. At the same time, we also hope them still
-%readable. Here we rename the variables with a regular format using the fresh function.
-
-Application of the semantic rules require generating a lot of fresh
-names, for different kind of variables. We could use a global name
-generator to guarantee unicity, but 
-at the same time, we also hope them still
-readable. Here we rename the variables with a regular format using the fresh function.
-More precisely, the fresh function generates a new name adding a
-suffix after the original name. The suffix contains three parts
-combined by a colon.
-
-\begin{definition}[Fresh variable]\label{fresh-variable}
-The format of \emph{fresh variable} (renaming) is defined as:
-``$\emph{prefix : tree\ index\ :\ counter}$''.
-\begin{itemize}
-   \item[$\bullet$] $prefix$ identifies the kind of the
-     variable. current kinds are: sva (SV action), ra (result action), hb (hole behavior).
-   \item[$\bullet$] $tree\ index$ is the index of the node containing the variable in the tree-like structure of the pNet.
-   \item[$\bullet$] $counter$ is the current value of the corresponding counter.
-\end{itemize}
-\end{definition}
-
-%\TODO{Option: Add the process and the vector ids ?}
-
-%$Prefix$ avoids the confusion between variables from different structures with the same name by attaching the type of the structure.
-$Tree\ index$ is given to every node of the pNets to mention which node the variable belongs to as pNets has a tree-like structure.
-To each node, the tree index is always a number sequence of the tree index of its higher level and the index of the node in this level at the last.
-$A\ set\ of\ counters$ is used to count the current times the SV, Hole, subnet invoked, or the number of possible OT generated to provide an identity.
-
-For example, in the running example, the first possible behavior of
-the hole, it doesn't have a name, only have the prefix ``hb''. The
-hole is the second subnets of the root node so its ``tree index'' is
-``12''. The fresh variable name is ``$\OTvar{:hb:12:1}$''. 
+
 \subsection{Variable managment}
@@
 
-Note that in principle, such an algebra correspond to a given
+Note that in principle, an action algebra corresponds to a given
 high-level language (e.g. a process algebra), and that the algebra
@@
 pNet semantics of each specific language.
-
-\paragraph{Algebra presentations}
-\begin{definition}
-  An Algebra Presentation is a pair $\mathcal{P}=<Sorts,Constrs,Ops>$ where:
-  \begin{itemize}
-  \item $Sorts$ is a set of Sort names
-    \footnote{Later we may want to extend this with Sort constructors,
-      like Array or Pair, but this is not needed now}
-  \item $Constrs$ is a set of constructor operators, with $Con$ the
-    constructor name, and arity: $arity(Con)=n \in \mathbb{N}$,
-    and with their signature and their associated selectors,
-    of the form: '$Con : (sel_1,sort_1), ... , (sel_n,sort_n) -> sort$'.
-    For each argument, the pair $(sel_i,sort_i)$ defines an auxiliary
-    operator of name $sel_i$ with signature $sel_i : sort -> sort_i$.
-    \item $Ops$ is a set of other (auxiliary) operators, with their
-      arity and signature, of the form: $Op : sort_1, ...  sort_n ->
-      sort$
-      \item $Constrs(sortname), Sels(sortname)$, respectively define the set of
-        constructors and selectors of sort $sortname$
-  \end{itemize}
-  All sorts and operator names must be distinct.\\
-  Amongst Constructors, those of arity 0 are called constants, and we
-  define $Consts(\mathcal{P}) = \{Con \in Constrs. arity(Con)=0\}$.
-\end{definition}
 

### 2018-01-16 2017-Xudong-SMT/FM-2018-extended.tex

@@
 \DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
-\usepackage{epsfig,color,subfigure,enumitem}
+\usepackage{epsfig,color,enumitem}
+\usepackage[%
+    font={small,sf},
+    labelfont=bf,
+    format=hang,    
+    format=plain,
+    margin=0pt,
+    width=0.8\textwidth,
+]{caption}
+\usepackage[list=true]{subcaption}
+
 \newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
@@
 
- %% \begin{figure}[t]
- %%   \centerline{\includegraphics[width=12cm]{XFIG/BIPspec-ArchFailureTimerMax}}
- %%   \caption{FailureTimer Architecture in BIP graphical syntax}  \label{schema:BIParchitecture}
- %% \end{figure}
-
  \begin{figure}[t]
-   \centerline{\includegraphics[width=12cm]{XFIG/FailureTimerPNET}}
-   \caption{FailureTimer pNet encoding\TODO{on peut gagner un peu en hauteur}}  \label{schema:BIParchitecture}
+   \centering
+   \includegraphics[width=\columnwidth]{XFIG/BIPspec-ArchFailureTimerMax-v2}
+   \caption{The BIP specification of the FailureTimer architecture}
+   \label{schema:ArchFailure:BIP}
+ \end{figure}
+%
+   %% \hfill
+%
+ \begin{figure}[t]
+   \centering
+   \includegraphics[width=\columnwidth]{XFIG/FailureTimerPNET}
+   \caption{pNet encoding of the FailureTimer architecture}
+   \label{schema:ArchFailure:pNet}
  \end{figure}
@@
 % \newpage
-\appendix
+%\appendix
 

### 2018-01-17 2017-Xudong-SMT/FM-2018-extended.tex
some details on encoding figure

@@
 \label{section:BIParchitectures}
-\TODO{Simon: can you do this in less than one page ? If you prefer,
-  merge with ``Running example'' may be easier to describe the syntax}
+\label{section:examples}
 
@@
 \begin{example}\emph{An open-transition.}
-  \TODO{a short explanation}
+  This transition is generated by application of vector \texttt{SV0}, synchronizing the initial actions of pLTSs \texttt{Failure} and \texttt{Timer}, with an action of the hole \texttt{B} equal to \texttt{fail}.
+Th elocal variable \texttt{t} of the \texttt{Timer} is assigned to its initial value \texttt{Max}.
   \label{OT:lotos-composed}
@@
 	{\{s0~{\xrightarrow{fail(true)}} ~s1, t0~{\xrightarrow{start(true)}} ~t1\}
-	  \{\xrightarrow{hb}\}, hb=fail(true) \land v=\underline{fail}, \{t := 4\}
+	  \{\xrightarrow{hb}\}, hb=fail(true) \land v=\underline{fail}, \{t := Max\}
         }

### 2018-01-17 2017-Xudong-SMT/checker.tex
cleaning git old synchro

@@
 \renewcommand{\P}{\mathcal P}
+\usepackage{listings}
+\lstset{basicstyle=\small}
+%\usepackage{algorithm} 
+%\usepackage{algpseudocode}
 
@@
 \begin{itemize}
-  \item for a given pNet: the presentation of the action algebra
-    (sorts, operators, constants), 
+  \item the presentation of the action algebra
+    (sorts and operators) that is defined for a given language (process calculus, or high level programming language),
+    \item for a given pNet, the set of local constants (actions or auxiliary data) that are used in the pLTSs,
     \item for each open transition: the declaration of variables, and
@@
 
-\section{Type system}
-%% The SMT solver Z3 already has conservative type rules and checks type safety in Horn logic. When translating the pNets into SMT-LIB language, pNets should also make sure that
-%% the term matching other term in SMT-LIB language will be correct in
-%% type checking. In next two section, we give out the presentation of
-%% the pNets and the type rules of them to ensure the type safety.
-The type system in pNets is quite simple, the expressions are built
-from variables, constants, and operators of a many-sorted algebra, and
-we only need simple first-order polymorphic types.
-Additionaly, for convenience, we want to introduce some ``generic''
-operators in the algebra, with an overloading mechanism; as these do
-not exist in SMTlib, we will have a specific translation mechanism.
-
 Note that in principle, such an algebra correspond to a given
@@
 
-\subsection{Algebra Presentations}
+\section{Algebra presentations}
+
+\begin{definition}
+  An Algebra Presentation is a pair $\mathcal{P}=<Sorts,Constrs,Ops>$ where:
+  \begin{itemize}
+  \item $Sorts$ is a set of Sort names
+    \footnote{Later we may want to extend this with Sort constructors,
+      like Array or Pair, but this is not needed now}
+  \item $Constrs$ is a set of constructor operators, with $Con$ the
+    constructor name, and arity: $arity(Con)=n \in \mathbb{N}$,
+    and with their signature and their associated selectors,
+    of the form: '$Con : (sel_1,sort_1), ... , (sel_n,sort_n) -> sort$'.
+    For each argument, the pair $(sel_i,sort_i)$ defines an auxiliary
+    operator of name $sel_i$ with signature $sel_i : sort -> sort_i$.
+    \item $Ops$ is a set of other (auxiliary) operators, with their
+      arity and signature, of the form: $Op : sort_1, ...  sort_n ->
+      sort$
+      \item $Constrs(sortname), Sels(sortname)$, respectively define the set of
+        constructors and selectors of sort $sortname$
+  \end{itemize}
+  All sorts and operator names must be distinct.\\
+  Amongst Constructors, those of arity 0 are called constants, and we
+  define $Consts(\mathcal{P}) = \{Con \in Constrs. arity(Con)=0\}$.
+\end{definition}
 
@@
 
+In addition, and for convenience, we provide one generic construct for
+parameterized actions named FUN, which can accept any number of
+arguments of any sort. The result type, though, can only be $Action$,
+in order to keep the type-checking simple (see next section).
+
 \begin{table}\caption{\label{Table:predefinedSorts}\leftline{Algebra Presentation: predefined Sorts
   and Operators}}
-	\begin{tabular}{p{4cm}p{8cm}}
+	\begin{tabular}{p{3cm}p{3cm}p{6cm}}
 		\hline\specialrule{0em}{1pt}{1pt}
-		Sort & Operator
+		Sort & Constructors & Other Operators
                 \\\specialrule{0em}{1pt}{1pt}
@@
 		Bool    			&
-                $\land,\ \lor,\ \texttt{true},\ \texttt{false}$
+                $\texttt{true},\ \texttt{false}$&
+                $\land,\ \lor$
                 \\\specialrule{0em}{1pt}{1pt} 
-		Action 			& \textsl{no predefined operator}
+		Action 			&  $\texttt{FUN}$ &
                 \\\specialrule{0em}{1pt}{1pt}
-		Int 				& $\ - \texttt{(unary)},\ +,\ -
-                \texttt{(binary)},\ \times,\ \div,\ {0, 1, ...} \in \texttt{Nat}$
+		Int 				&
+                ${0, \{i, -i\}_{i \in \texttt{Nat}}}$  &
+                $- \texttt{(unary)},\ +,\ -
+                \texttt{(binary)},\ \times,\ \div, \texttt{etc.}$
                 \\\specialrule{0em}{1pt}{1pt}
-                \textsl{for any sort} & $=,\ \ne$
+                \textsl{for any sort} & & $=,\ \ne$
 		\\\hline
@@
 declare more sorts and operators, using our pNet API.
-As an example, the CCS action algebra include:
+As an example, a (value-passing) CCS action algebra, where we assume a
+single auxiliary value domain ``Data'', can be defined as:
 
-\subsection{Type Rule}
-The environment is a set of variables with their own types like $x_1 : A_1, ...
-, x_n : A_n$.
-And use dom$(\Gamma)$ dedicate the collection of $x_1, ...
-, x_n$.
-Let $\mathcal{P}$ to be the presentation of the pNet.
-\begin{table}\caption{\leftline{Judgments for Open pNets}}
+\begin{example}
+  \begin{itemize}
+  \item $Sorts_{CCS} = \{Action, Channel, Data, Int, Bool\}$
+  \item $Constrs_{CCS} =\\
+    \texttt{Emit}: 2, \{(Chan\_E:Channel),(Value\_E:Data)\}->Action\\
+    \texttt{Receive}: 2, \{(Chan\_R:Channel),(Value\_R:Data)\}->Action\\
+    \texttt{Tau}: 0, \{\}-> Action\\
+    \texttt{... and all predefined operators}$
+  \end{itemize}
+\end{example}
+
+\TODO{[Xudong]: Give an example of defining $Tau$ and $Emit$ using the (new
+  version of) the API}
+
+\section{Expressions}
+Once an algebra presentation is defined, we can construct expressions
+of the term algebra, using variables and operators:
+
+\begin{definition}
+  Let $\mathcal{V}$ be a set of variables. The Term Algebra
+  $\Sigma_{\mathcal{P},\mathcal{V}}$ is the set of:
+  \begin{itemize}
+  \item variables $x \in \mathcal{V}$
+  \item terms (or expressions) $op (arg_1, ... , arg_n)$ with $op$ an operator in
+  $\mathcal{P}$ of arity $n$, and each $arg_i$ an expression.
+  \end{itemize} 
+\end{definition}
+
+\subsection{Constants and variables in pNets and in open transitions}
+
+In addition to the objects defined in the Algebra Presentation, there are
+specific objects that are introduced by the pNet construction, and by
+the semantic rules used to build the open transitions and their
+predicates. This includes, for a pNet $pnet$
+\begin{itemize}
+\item $Const(pnet)$: Constants from the pLTSs (controllers) transitions: these are
+  new constant constructors, usualy of sort Action, local to an
+  instance of a controller. The pNet definition requires that all
+  these constants are distinct from each other.
+\item $SVars(pnet)$: State variables of the controllers. Here also they are required
+  to be distinct from those of other controllers.
+\item $IVars(pnet)$: Input variables of the controllers.
+\item $FVars(pnet,ot)$: Several kinds of ``fresh'' variables, created by application of
+  rule Tr2, during the construction of each open transition $ot$:
+  Action variables for the behavior of holes and the 
+  resulting actions of transitions, variables created during the cloning
+  of synchronisation vectors.
+\end{itemize}
+
+\def\EPres{\mathcal{P}}
+\def\EEnv{\Gamma}
+
+All variable sets above include their sort.
+To define the typing rules for expressions and the translation
+functions, for any pNet $pnet$ and open transition $ot$, we define an
+extended presentation $\EPres_{pnet}$ and environment $\EEnv_{pnet,ot}$ that includes all of the
+objects above:
+
+\begin{definition}
+  Given an algebra presentation $\mathcal{P}_{pnet}=<Sorts,Constrs,Ops>$ and a pNet $pnet$, we
+  construct:
+  \begin{itemize}
+  \item An extended presentation $\EPres_{pnet}<Sorts,Constrs \cup Const(pnet),Ops>$.
+  \item For a given open transition $ot$, an environment
+    $\EEnv_{pnet,ot}=SVars(pnet) \cup IVars(pnet) \cup FVars(pnet,ot)$. 
+  \end{itemize} 
+\end{definition}
+
+\subsection{Well-formed and well-typed expressions}
+
+The purpose of this section is to define static semantic notions that
+will guarantee that the translation to the SMT language will be
+correct, i.e. will not yield errors at runtime. This includes
+well-formness (all sorts, operators, variables are defined, and
+expressions respect the arity of operators), and typing rules.
+
+\begin{definition}
+  Given a presentation $\EPres$ (possibly extended) and an environment $\EEnv$:
+  \begin{itemize}
+  \item $\EEnv$ is well-formed if all sorts in $\EEnv$ are
+    defined in $\EPres$
+  \item an expression is well-formed if all its operators are defined
+    in $\EPres$, and used with the proper arity, and all its
+    variables are defined in $\EEnv$
+  \item an expression is well-typed if it can be typed by the typing
+    rules in table \ref{table:typing-rules}
+  \end{itemize}
+\end{definition}
+
+The following judgment, and the typing rules in table
+\ref{table:typing-rules} can be used to check both the wellformedness
+and well-typing of expressions in a pNet or in an open transition,
+given the corresponding $\EPres$ and $\EEnv$.
+
+%\begin{table}\caption{\leftline{Typing judgment for Expressions in Open pNets}}
+\vspace{1ex}
+\noindent
 \begin{tabular}{p{5cm}p{7cm}}
 		\hline\specialrule{0em}{3pt}{3pt}
-		$\Gamma \vdash \diamond$ 					& $\Gamma$ is a well-formed environment 					\\\specialrule{0em}{1pt}{1pt}
-		$\Gamma \vdash A$ 							& A is a well-formed type in $\Gamma$	 					\\\specialrule{0em}{1pt}{1pt}
-		$\Gamma \vdash M: A$ 						& M is a well-formed term of type A in $\Gamma$			\\\specialrule{0em}{1pt}{1pt}
+%%		$\EEnv \vdash \diamond$ 					& $\EEnv$ is a well-formed environment 					\\\specialrule{0em}{1pt}{1pt}
+%%		$\EEnv \vdash A$ 							& A is a well-formed type in $\EEnv$	 					\\\specialrule{0em}{1pt}{1pt}
+		$\EPres,\EEnv \vdash M: A$
+                & M is a well-formed term of type A in $\EPres,\EEnv$			\\\specialrule{0em}{1pt}{1pt}
 		\specialrule{0em}{3pt}{3pt}\hline
 	\end{tabular}
-\end{table}
+%\end{table}
 
 \begin{table}\caption{\leftline{Type Rules for Open pNets}}
+  \label{table:typing-rules}
 	\begin{tabular}{p{5cm}p{5cm}p{2.5cm}}
 		\hline\specialrule{0em}{3pt}{3pt}
-		(Env $\varnothing$) 								
-		& 										
-		&					\\\specialrule{0em}{1pt}{1pt}
-            $\dfrac{ }{\varnothing \vdash \diamond}$			
-            & %$\dfrac{\Gamma \vdash A ~~ x\ }{\varnothing \vdash \diamond}$
-            &					\\\specialrule{0em}{3pt}{3pt}
-		(Type Bool) 										
-		&(Type Action) 						
-		&(Type Int)			\\\specialrule{0em}{1pt}{1pt}
-		$\dfrac{\mathcal{P} \vdash Bool~~\Gamma \vdash \diamond}{\mathcal{P},\Gamma \vdash Bool}$ 
-		& $\dfrac{\mathcal{P} \vdash Action~~\Gamma \vdash \diamond}{\mathcal{P},\Gamma \vdash Action}$ 
-		& $\dfrac{\mathcal{P} \vdash Int~~\Gamma \vdash \diamond}{\mathcal{P},\Gamma \vdash Int}$        \\\specialrule{0em}{3pt}{3pt}
+		%% (Env $\varnothing$) 								
+		%% & 										
+		%% &					\\\specialrule{0em}{1pt}{1pt}
+            %% $\dfrac{ }{\varnothing \vdash \diamond}$			
+            %% & %$\dfrac{\EEnv \vdash A ~~ x\ }{\varnothing \vdash \diamond}$
+            %% &					\\\specialrule{0em}{3pt}{3pt}
+		%% (Type Bool) 										
+		%% &(Type Action) 						
+		%% &(Type Int)			\\\specialrule{0em}{1pt}{1pt}
+		%% $\dfrac{\EPres \vdash Bool~~\EEnv \vdash \diamond}{\EPres,\EEnv \vdash Bool}$ 
+		%% & $\dfrac{\EPres \vdash Action~~\EEnv \vdash \diamond}{\EPres,\EEnv \vdash Action}$ 
+		%% & $\dfrac{\EPres \vdash Int~~\EEnv \vdash \diamond}{\EPres,\EEnv \vdash Int}$        \\\specialrule{0em}{3pt}{3pt}
 		(Var x) 										
@@
 		&			\\\specialrule{0em}{1pt}{1pt}
-		$\dfrac{\mathcal{P} \vdash A~~\Gamma \vdash x:A}{\mathcal{P},\Gamma \vdash x:A}$ 
+		$\dfrac{\EEnv \vdash x:A}{\EPres,\EEnv \vdash x:A}$ 
 		&  
@@
 		& 			\\\specialrule{0em}{3pt}{3pt}
-		$\dfrac{\mathcal{P} \vdash BinOp :: ty1, ty1 \rightarrow ty2 ~~\Gamma \vdash x_1:ty1 ~~\Gamma \vdash x_2:ty1}{\mathcal{P},\Gamma \vdash x_1 ~BinOp~ x_2:ty2}$ 
+		$\dfrac{\EPres \vdash BinOp :: ty1, ty1 \rightarrow ty2 ~~\EEnv \vdash x_1:ty1 ~~\EEnv \vdash x_2:ty1}{\EPres,\EEnv \vdash x_1 ~BinOp~ x_2:ty2}$ 
 		& 
@@
 		& 			\\\specialrule{0em}{3pt}{3pt}
-		$\dfrac{\mathcal{P} \vdash UnOp :: ty1 \rightarrow ty2 ~~\Gamma \vdash x:ty1}{\mathcal{P},\Gamma \vdash Unop~x:ty2}$   
+		$\dfrac{\EPres \vdash UnOp :: ty1 \rightarrow ty2 ~~\EEnv \vdash x:ty1}{\EPres,\EEnv \vdash Unop~x:ty2}$   
 		&&       		\\\specialrule{0em}{5pt}{5pt}
@@
 		&
-                                         \\\specialrule{0em}{1pt}{1pt}
-		\multicolumn{2}{l}{(Note: I removed the $~~\mathcal{P} \vdash \ne :: A, A \rightarrow Bool$)}
-
-		&                        \\\specialrule{0em}{3pt}{3pt}
-		$\dfrac{\mathcal{P} \vdash A  ~~\Gamma \vdash x_1:A ~~\Gamma \vdash x_2:A}{\mathcal{P},\Gamma \vdash x_1 = x_2:Bool}$ 
+                                         \\\specialrule{0em}{3pt}{3pt}
+		$\dfrac{\EPres \vdash A  ~~\EEnv \vdash x_1:A ~~\EEnv \vdash x_2:A}{\EPres,\EEnv \vdash x_1 = x_2:Bool}$ 
 		& 
-		$\dfrac{\mathcal{P} \vdash A  ~~\Gamma \vdash x_1:A ~~\Gamma \vdash x_2:A}{\mathcal{P},\Gamma \vdash x_1 \ne x_2:Bool}$
+		$\dfrac{\EPres \vdash A  ~~\EEnv \vdash x_1:A ~~\EEnv \vdash x_2:A}{\EPres,\EEnv \vdash x_1 \ne x_2:Bool}$
 
@@
 		& 			\\\specialrule{0em}{3pt}{3pt}
-		$\dfrac{\mathcal{P} \vdash \texttt{FUN} :: A_1,...,A_n \rightarrow A ~~\mathcal{P} \vdash A_1~~...~~\mathcal{P} \vdash A_n ~~\Gamma \vdash x_1:A_1~~...~~\Gamma \vdash x_n:A_n}{\mathcal{P},\Gamma \vdash \texttt{FUN}(x_1,...,x_n):A}$
+		$\dfrac{\EPres \vdash \texttt{FUN} :: A_1,...,A_n \rightarrow Action ~~\EPres \vdash A_1~~...~~\EPres \vdash A_n ~~\EEnv \vdash x_1:A_1~~...~~\EEnv \vdash x_n:A_n}{\EPres,\EEnv \vdash \texttt{FUN}(x_1,...,x_n):Action}$
 		& 
@@
 
+\begin{remark}
+  These rules provide a simple type-checking algorithm: if all
+  variables in an expression are known in $\EEnv$, then a bottom-up
+  application of the rules will decide whether the expression is
+  well-typed, and compute the type of each sub-expression.
+\end{remark}
+
 \subsection{Map to SMT-LIB language}
-The pNet semantics can be full translated into SMT-LIB language, though some difference on defining functions exist.
-\begin{table}\caption{\leftline{Mapping}}
+The pNet elements, as defined above, can be full translated into
+SMT-LIB language, but there are a number of differences in the
+structure of the models/langages, so the translation is not trivial.
+
+In this section we shall define separately the translation of the
+(extended) algebra presentation for one pNet (so it will be fixed for
+the study of one use-case); and the translation of each predicate in
+the context of an open-transition of this pNet.
+
+\def\translate{~\lhook\joinrel\longrightarrow}
+
+\vspace{1ex}\noindent
+%\begin{table}\caption{\leftline{Mapping}}
 	\begin{tabular}{p{3cm}p{9cm}}
-		\hline\specialrule{0em}{5pt}{5pt}			
+		\hline\specialrule{0em}{1pt}{1pt}			
 		(Presentation)							
-		&								\\\specialrule{0em}{5pt}{5pt}		
-		&$Sort \lhook\joinrel\longrightarrow$	declare-datatypes				\\\specialrule{0em}{3pt}{3pt}
-		&$Operator \lhook\joinrel\longrightarrow$	declare-function		\\\specialrule{0em}{3pt}{3pt}
-		(Checking)							
-		&								\\\specialrule{0em}{5pt}{5pt}
-		&$dom(\Gamma) \lhook\joinrel\longrightarrow$	declare-const		\\\specialrule{0em}{3pt}{3pt}
-		&$Pred \lhook\joinrel\longrightarrow$	 assert		\\\specialrule{0em}{3pt}{3pt}
-		(Expressions)							
-		&								\\\specialrule{0em}{5pt}{5pt}
-		&$\texttt{FUN}(x_1,...,x_n)$		\\\specialrule{0em}{3pt}{3pt}
-		&$x_1- x_n$  $~~~~~~~\lhook\joinrel\longrightarrow$ declare-function	\\\specialrule{0em}{3pt}{3pt}
-		&$...$	\\\specialrule{0em}{3pt}{3pt}
-		\specialrule{0em}{5pt}{5pt}\hline
+		&								\\\specialrule{0em}{1pt}{1pt}		
+		&$Sorts \& Constructors \translate$	declare-datatypes				\\\specialrule{0em}{1pt}{1pt}
+		&$Operators \lhook\joinrel\longrightarrow$	declare-function		\\\specialrule{0em}{1pt}{1pt}
+		(Predicate)							
+		&								\\\specialrule{0em}{1pt}{1pt}
+		&$\EEnv ~~\lhook\joinrel\longrightarrow$	declare-const		\\\specialrule{0em}{1pt}{1pt}
+		&$Pred ~~\lhook\joinrel\longrightarrow$	 assert		\\\specialrule{0em}{1pt}{1pt}
+		&$\texttt{FUN}(x_1,...,x_n)$		\\\specialrule{0em}{1pt}{1pt}
+		&$\texttt{pNet expression} ~~\lhook\joinrel\longrightarrow$ SMTLib expression	\\\specialrule{0em}{1pt}{1pt}
+		&$...$	\\\specialrule{0em}{1pt}{1pt}
+		\specialrule{0em}{1pt}{1pt}\hline
 	\end{tabular}
-\end{table}
+%\end{table}
 
-\paragraph{Translation} from pNets informations into SMT-LIB language format is corresponded with the mapping rules.
-\subsubsection{Sort}
-There are several basic Sorts already defined in the presentation and users can declare more customized Sorts.
-In addition, Bool and Int type is also Z3 default datatypes.
-Sorts only provide their names to the datatype constructor in Z3, the more content will be added according to the Operators in the presentation.\\\\
-\centerline{$\texttt{(declare-datatypes\ ()\ (($SortName$\ ...\ )))}$}
-%(declare-datatypes () ((SortName ... )))
-\subsubsection{FUN function}
-The signature of the FUN operators are defined by users. But they still have a fixed format.\\\\
-\centerline{$\texttt{FUN} :: Type_1, ... ,Type_n \longrightarrow Type$}\\\\
-%(declare-fun FUN (TypeName_1, ... ,TypeName_n) TypeName)
-The types of all the arguments are given to the Z3, so does the return type, but written at another place.  We use a suffix after the "FUN" name to distinct different FUN operators.\\\\
-\centerline{$\texttt{(declare-fun\ FUN\_Type1...\_TypeN\_Type\ ($Type_1$\ ... \ $Type_n$)\ $Type$)}$}
+\smallskip
+\ERIC{My plan here is to provide the translation principles as some
+  high-level pseudo code, together with precise definition of the
+  translation functions of a presentation+environment, and of a
+  predicate (including expressions)}
+
+In the following definitions, we use abstract functions corresponding to
+SMTlib/Z3 constructs. In practice they can be implemented either as
+SMTLib scripting programs, or as calls to the Z3 java API.
+
+\subsection{Presentation Translation}
+We define here the translation of the algebra presentation, extended
+with the constant operators collected from the pNet. It produces the
+declaration of sorts (excepted Bool and Int) with their constructors
+and selectors as \texttt{declare-datatypes}, and the declaration of
+other operators as \texttt{declare-function} constructs.
+For sorts, we must distinguish the case of mutually defined sorts
+(e.g. edges and vertices in a graph), that must be declared within a
+single \texttt{declare-datatypes} construct. For this we define:
+
+\begin{definition}
+Define the (strict) order "is-using" between sorts $S1 is-using S2$ iff $S2$
+occurs as the sort of one argument in the constructors of $S1$.
+\end{definition}
+
+\TODO{[Xudong: this is certainly obsolete?] At the same time, we have
+  several internal lists (actually hash 
+  maps) \texttt{exprs}, \texttt{funcDecls}, \texttt{sortDatatypes} to
+  store the generated Z3 objects with their names for later proofs.}
+
+\begin{lstlisting}
+Let Pres = <Sorts, Constrs, Ops> an extended presentation
+(i.e. including the constants from the pnet),
+- define MySorts = Sorts \ {Bool, Int}
+- compute the strongly connected components in the graph
+  of MySorts with respect to the relation is-using
+- for each SCC in this graph, construct: 
+  dataype-declaration = TrPresentation (Pres, SCC)
+- for each other operator op in Ops, construct:
+  function-declaration = TrPresentation (Pres, op)
+\end{lstlisting}
+
+%\begin{table}\caption{\leftline{Rules for TrPresentation}}
+%  \label{table:TrPresentation}
+\noindent
+\begin{tabular}{p{5cm}p{5cm}p{2.5cm}}
+		\hline\specialrule{0em}{3pt}{3pt}
+		\multicolumn{2}{l}{One datatype declaration for each SCC}
+
+		& 			\\\specialrule{0em}{1pt}{1pt}
+		$\dfrac{name=name(Sort) \qquad constrs=Constrs(name) %\qquad sels=Sels(name)
+                  \translate constrs}
+                       {SCC \translate
+                  \texttt{(declare-datatypes () $name$ (map $\translate constrs$))}}$
+
+		&&       		\\\specialrule{0em}{1pt}{1pt}
+		\multicolumn{2}{l}{Constants: }
+
+		& 			\\\specialrule{0em}{1pt}{1pt}
+		$\dfrac{arity(constr)=0}
+                       {constr \translate \texttt{name($constr$)}}$
+
+		&&       		\\\specialrule{0em}{1pt}{1pt}
+		\multicolumn{2}{l}{Other constructors: }
+
+		& 			\\\specialrule{0em}{1pt}{1pt}
+		$\dfrac{n = arity(constr) \neq 0 \qquad |sels|=n
+                  \qquad sels =  BuildSels(constr)}
+                       {constr \translate \texttt{(name($constr$) . sels)}}$
+
+		&&       		\\\specialrule{0em}{1pt}{1pt}
+		\multicolumn{2}{l}{Other operators: }
+
+		& 			\\\specialrule{0em}{1pt}{1pt}
+		$\dfrac{op : sort_1, ..., sort_n : sort}
+                       {op \translate \texttt{(declare-fun name($op$) ($sortname_1
+                           ... sortname_n$) $sortname$)}}$
+
+		&&       		\\\specialrule{0em}{1pt}{1pt}
+		\multicolumn{2}{l}{Special case of FUN: }
+
+		& 			\\\specialrule{0em}{1pt}{1pt}
+		$\dfrac{}
+                       {FUN \translate \texttt{map $\translate CollectFunTypes(pNet)$ }}$
+
+		&&       		\\\specialrule{0em}{1pt}{1pt}
+		$\dfrac{}
+                       {argstypes \translate \texttt{(declare-fun
+                           $BuildFunInstance(argstypes)$ (map name
+                           $argstypes$) Action) }}$
+
+		&&       		\\\specialrule{0em}{1pt}{1pt}
+		\hline
+\end{tabular}
+%\end{table}
+
+\smallskip
+Where:
+\begin{itemize}
+  \item the $BuildSels$ function, for a constructor with $n$ arguments,
+argument sorts $sort_i$, and selector names $sel_i$, builds the list
+$\{(sel_i, sort_i)\}_{i\in[1..n]}$.
+\item the $CollectFunTypes$ function collects all possible instances
+  of the overloaded FUN argument types found in the pNet, as computed by the typing
+  rules; and $BuildFunInstance$ use these argument types as suffixes
+  to disembiguate 
+\end{itemize}
+
+\begin{example}
+  For the CCS presentation above, we would get (in SMTLib syntax):
+\begin{lstlisting}
+  (declare-datatypes Data ())
+  (declare-datatypes Channel ())
+  (declare-datatypes ()
+      ((Action (Emit (Chan\_E Channel) (Value\_E Data))
+               (Receive (Chan\_R Channel) (Value\_R Data))
+               Tau )))
+  \end{lstlisting}
+\end{example}
+
+\TODO{Need to add an exemple with 2 instances of FUN}
+
+\subsection{Predicate translation}
+
+\QIN{Each time we submit each open transition to Z3 module, we translate
+  its predicate into Z3 language format and send it for satisfiability
+  checking. Every term of the predicate is declared as an
+  \texttt{assert} in Z3. A constant action or a parameterized
+  expression is easy to get from the internal list storing the objects
+  while all the variables are not declared at the beginning. So we
+  declare them before the submission of a predicate term with the API
+  method conducting \texttt{declare-const}.}
+
+The second part of the translation function is called for each open
+transition. More precisely we need here:
+
+\begin{lstlisting}
+Let Pres = <Sorts, Constrs, Ops> be the extended presentation
+and OT = <Leaves, Holes, Pred, Assign> an open transition.
+- compute the environment $\EEnv=\EEnv_{pnet,OT}$ collecting
+all variables used in OT
+- check that all pLTS labels (action, guard, assignement) in
+the transition, the OT predicate, and the OT assignments are
+well-formed and well-typed
+- for each variable $v$ in $\EEnv$, construct:
+  define-const = TrPredicate ($\EEnv,v$)
+- turn the predicate into conjunctive normal form
+- for each conjunct $P_i$ in the predicate, construct:
+  assert = TrPredicate $(P_i)$
+\end{lstlisting}
+
+\noindent
+\begin{tabular}{p{5cm}p{5cm}p{2.5cm}}
+		\hline\specialrule{0em}{3pt}{3pt}
+		\multicolumn{2}{l}{Variables}
+
+		& 			\\\specialrule{0em}{1pt}{1pt}
+		$\dfrac{\EEnv \vdash x:A }
+                       {x \translate \texttt{(declare-const x A)}}$
+
+		&&       		\\\specialrule{0em}{1pt}{1pt}
+		\multicolumn{2}{l}{Predicate conjunct: }
+
+		& 			\\\specialrule{0em}{1pt}{1pt}
+		$\dfrac{}
+                       {P_i \translate \texttt{(assert ... }}$
+
+		&&       		\\\specialrule{0em}{1pt}{1pt}
+		\multicolumn{3}{p{12cm}}{To be completed with translation of
+                expressions, including special cases for EQ, NOT\_EQ,
+                and FUN }
+
+		 			\\\specialrule{0em}{1pt}{1pt}
+		\hline
+\end{tabular}
+%\end{table}
 
 \section{Submission to Z3}
+\TODO{Do we still need that ? Maybe rather something linking my
+  "abstract SMTLib functions" with both SMTLib python code, and Z3 API
+  methods.}
+
 \subsection{Z3 Notations}
@@
 
-\subsection{Submission of Algebra}
-Before the submission of the open transitions to Z3, the user-inputed algebra of the pNet should be known at first.
-It gives Z3 informations of the sorts of the expression and the operators, corresponding to the
-\texttt{declare-datatypes} and \texttt{declare-function}.
-We declare the algebra in Z3 logic through Z3 API methods having the same effect as the notations.
-At the same time, we have several internal lists (actually hash maps) \texttt{exprs}, \texttt{funcDecls}, \texttt{sortDatatypes} to store the generated Z3 objects with their names for later proofs.
-
-\subsection{Submission of Open Transitions}
-Each time we submit each open transition to Z3 module, we translate its predicate into Z3 language format and send it for satisfiability checking.
-Every term of the predicate is declared as an \texttt{assert} in Z3.
-A constant action or a parameterized expression is easy to get from the internal list storing the objects while all the variables are not declared at the beginning.
-So we declare them before the submission of a predicate term with the API method conducting \texttt{declare-const}.
-
 \subsection{Other works}
 \paragraph{Quantifier}
-\paragraph{Filter the State without Precursor}
 

### 2018-01-17 2017-Xudong-SMT/FM-2018-extended.tex
pages 11-13

@@
 %\usepackage{setspace}
+\usepackage{enumitem}
+\setlist{nolistsep}
 %\usepackage{indentfirst}
@@
 
-pNets can encode naturally the notion of input actions as found e.g. in value-passing CCS
-\cite{Milner89} or of usual point-to-point message passing calculi, but it also allows
+pNets can encode naturally the notion of input actions as found
+e.g. in value-passing CCS 
+\cite{Milner89} or of usual point-to-point message passing calculi,
+but it also allows 
 for more general mechanisms, like gate negotiation in Lotos, or broadcast
@@
 In practice, the parameterization of the pNet model by some specific
-action is realized through the definition of an ``algebra
-presentation''. It will be used to define formaly a notion of
-well-formness of a pNet system, and the translation of the pNet
+action algebra is realized by the definition of an ``algebra
+presentation''. It will be used to check the
+well-formness of a pNet system, and to define the translation of the pNet
 semantics into the SMT engine input language.
@@
   An Algebra Presentation is a pair $\mathcal{P}=<Sorts,Constrs,Ops>$ where:
+
   \begin{itemize}
@@
 \end{definition}
+
+Sorts \texttt{Bool} and \texttt{Int} are predefined with standard operators.
+Sort \texttt{Action} also, with a constructor \texttt{Synchro} denoting
+a synchronized action, i.e. an ``internal'' action that cannot be
+further synchronized with the environment. It also comes with an
+overloaded \texttt{FUN} constructor, used to build actions with
+arguments, that will be instanciated to the required sorts for a given
+pNet.
+
+\begin{table}\caption{\label{table:BIPalgebra}\leftline{Algebra
+      Presentation: predefined and BIP Sorts and Operators}}
+	\begin{tabular}{p{3cm}p{3cm}p{6cm}}
+		\hline\specialrule{0em}{1pt}{1pt}
+		Sort & Constructors & Other Operators
+                \\\specialrule{0em}{1pt}{1pt}
+		\hline\specialrule{0em}{3pt}{3pt}
+		Bool    			&
+                $\texttt{true},\ \texttt{false}$&
+                $\land,\ \lor,\ \neg,\ \implies,\ =,\ \ne$
+                \\\specialrule{0em}{1pt}{1pt} 
+		Action 			&  $\texttt{Synchro},\ \texttt{FUN\_Action\_Bool}$ &
+                \\\specialrule{0em}{1pt}{1pt}
+		Int 				&
+                ${0, \{i, -i\}_{i \in \texttt{Nat}}}$  &
+                $- \texttt{(unary)},\ +,\ -
+                \texttt{(binary)},\ \times,\ \div, \texttt{etc.}$
+%                \\\specialrule{0em}{1pt}{1pt}
+%                \textsl{for any sort} & & $=,\ \ne$
+		\\\hline
+	\end{tabular}
+\end{table}
 
@@
 
-\begin{example}\emph{An open-transition.}
-  This transition is generated by application of vector \texttt{SV0}, synchronizing the initial actions of pLTSs \texttt{Failure} and \texttt{Timer}, with an action of the hole \texttt{B} equal to \texttt{fail}.
-Th elocal variable \texttt{t} of the \texttt{Timer} is assigned to its initial value \texttt{Max}.
+\begin{example}\emph{An open transition.}
+  This transition is generated by application of vector \texttt{SV0},
+  synchronizing the initial actions of pLTSs \texttt{Failure} and
+  \texttt{Timer}, with an action of the hole \texttt{B} equal to
+  \texttt{fail}. The local variable \texttt{t} of the \texttt{Timer}
+  is assigned to its initial value \texttt{Max}. \TODO{may be the
+    place to mention the ``fresh variable'' names, rather than in th
+    eZ3 syntax figure}
   \label{OT:lotos-composed}
@@
   \caption{Open Automaton Generation}
+  \label{alg1}
 \begin{algorithmic}[1]
@@
 \caption{MakeTransitions()}
+  \label{alg2}
 \begin{algorithmic}[1]
@@
 %composed into the predicate $a \neq l$.
-
+\TODO{a more significant example, including state-variable assignements
+  ??}
 \begin{figure}[h]
@@
 executes a ``$start$''. The chosen synchronization
-vector does not match with these actions,as appears in the predicate
+vector does not match with these actions, as appears in the predicate
 fragment ``$\OTvar{resume(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}$''.
-Fig.~\ref{schema:smt-lib} shows the translation of this OT predicate
-in the SMTlib syntax. Here we display also the proof generated by Z3,
-though in practice our tool only needs the brute information ``sat'' or ``unsat''.
 
@@
 may depend on the specific theory of the action algebra. 
-We use the SMT solver Z3 to check the predicate of the result open transitions, 
-it will return whether the predicate is satisfiable or not.
 The ``Modulo Theory'' part of SMT solvers is important here, so that
@@
 
-\TODO{Eric: Replace by (excerpts of) the formal version, from appendix, and reduce to less than one page}
-
-\paragraph{Presentation of algebra}
-
-%% As seen in section
-%% \ref{section:pnets}, the \emph{term algebra} used to express the
-%% action expressions and data parameters is left open in
-%% the pNet definition.
-
-%% So, for a given language, we now need to specify its data and action
-%% domains, giving them an abstract syntax (sorts, constructors, operators,
-%% and predicates). We call this a \emph{Presentation}.
-%% We also define a concrete syntax, that will be used for
-%% pretty-printing, but also for translating the presentation, and the
-%% predicates, into Z3 syntax (see the ``declare-datatypes'' statement in
-%% Fig~\ref{schema:smt-lib}).
-
-%% An algebra presentation contains:
-
-%% \begin{itemize}
-%% 	\item Sorts: Constants sets of the algebra or types of the data
-%%           and actions (integer and boolean sort are implicitly
-%%           declared).  There \emph{must} be one sort for actions, and
-%%           eventually others for the types of data
-%%           parameters. In the LOTOS example, 
-%%           we have the $Action$ sort: $\OTvar{Action = } \{ l, \delta,
-%%           r, p, q, acc \} .$
-
-%% 	\item Operators:
-%%           %Operators used to construct action expressions; they are
-%%           constructors and predicates for data and action sorts. For
-%%           instance, in our LOTOS example, we
-%%           have a generic action constructor ``$ACT$'', taking as
-%%           argument an action litteral and a data parameter, declared as:
-%%           $\OTvar{ACT:}\OTvar{< Action, Data >} \rightarrow \OTvar{Action.}$, 
-%%         \item Constants: The satisfiability solver need to know which
-%%           actions in the pLTS behaviors are constants (like the $l$, $\delta$, 
-%%           $r$ of the controllers in running example). 
-%%           For a given pNet system, the sort $Action$ will include all
-%%           these constants.
-%% \end{itemize}
-
-\paragraph{Interaction with Z3}
-%\TODO{1. example input of Z3 in SMT-LIB.[DONE] 2. software architecture.[DONE]}
-%There are several ways to interact with the Z3 solver. 
-%It is possible to use Z3 interactively using the SMT-LIB
-%(Python-based) language. 
+As the last step of \ref{alg1}, we use the SMT solver Z3 to check the
+satisfiability of each open transitions. More precisely, we translate
+the OT predicate into a SMTlib assertion, in the context provided by
+the possible state variable assignments in the source state. In this
+section we describe the translation of the algebra presentation, of
+assignments, and of the predicates.
+
 From inside our algorithm code, we submit satisfiability requests to
 Z3 using its JAVA API. Here for readability, we
-show the Z3 code using its SMT-LIB input language. As an
-example in
-Fig~\ref{schema:smt-lib}, we show the input for checking the
-transition of Fig.~\ref{schema:unsat-ot}. It contains the declaration
-of the LOTOS action algebra types 
+show the Z3 code using its SMT-LIB input language.
+
+Fig.~\ref{schema:smt-lib} shows the translation of the
+transition of Fig.~\ref{schema:unsat-ot}
+in the SMTlib syntax.
+It contains the declaration
+of the BIP action algebra sorts 
 and constructors, then the declaration of variables, and finally the
 predicate to be checked, encoded as a set of assertions.
-%% Generally, some $datatypes$ are declared to input the sorts, while here
-%% we only declare one $datatypes$ named $Action$ to involve all the
-%% constant actions. Then we input the predicate of this open transition
-%% in two parts: the variables contained in the predicate are declared
-%% first, then the terms of predicate are inputed as $assertions$ one by
-%% one. 
-The result "unsat" in the output is just what we expected.
-
-%\TODO{edit the figure to make it smaller in height [DONE]}
-
-%We present the architecture of the interaction with Z3 in
-%Fig~\ref{schema:interaction}.
-%For each OT generated at the toplevel of a pNet, the predicate must be
-%submitted for satisfiability check to Z3. For that we need to
-%translate into Z3 (Java-API) syntax, both the elements of the action
-%algebra, and the predicates itself, including the encoding of the
-%variable assignments (the Post part).
-%
-%The $presentation$ of the action algebra
-%is declared at the beginning of the algorithm as the $sorts$ and the
-%$operators$ will be used throughout the whole algorithm. It is
-%translated into $datatypes$ and $functions$ then submitted to the Z3
-%at the same time. Each candidate predicate will then be translated
-%into $assertions$ before submitted to Z3 after the algorithm
-%computing out all the possible open transitions, they act as
-%intermediate results there. Together with the $datatypes$ and
-%$functions$, the $assertions$ are used to check the satisfiability of
-%the predicate in Z3.
+Here we display also the proof generated by Z3,
+though in practice our tool only needs the brute information ``sat''
+or ``unsat''. The result "unsat" in the output is just what we expected.
 
@@
 \paragraph{Translation of Action algebra presentation}
-\TODO{Exerpt of the formalisation}
-The $datatypes$ are declared according to the $sorts$ the users
-declared in the $presentation$. If the return type of the $functions$
-is one of the $datatypes$, we add this $function$ to the $datatypes$ declaration.
-So when we declare the operator ACT we illustrated in section 4.1, it
-will be just declared together with the constants like :\\
-\centerline{$\OTvar{(ACT\ (action3\ Action)(data\ Int))}$}
-
-The $functions$ can also be declared independently, it usually applies to functions returning integer or boolean, in the format like:\\
-\centerline{$\OTvar{(declare\text{-}fun\ MAX\ (Int\ Int)\ Int)}$}
-
-%Although in Fig~\ref{schema:smt-lib} we have not declared $functions$ outside of $datatypes$, there still exists $functions$ declared independently.
-The input and output types of the $function$ are also determined by the construct of the  $operators$ in the presentation.
-For example, we define a new operator to present the equation between two actions in LOTOS example $\text{EQUAL}$ in the format likes:
-%
-%\[EQUAL: \quad < Action , Action > \rightarrow Bool .\]
-%
-%It will be translated into the Z3 statement: 
-%
-%\[\text{(declare-fun\ EQUAL\ (Action\ Action)\ Bool) .}\]
+In appendix \ref{appendix:mapsmt} we define formaly a condition of
+well-formness of an algebra presentation, and its translation into
+SMTlib declarations (\texttt{declare-datatypes} and
+\texttt{declare-fun}). It ensures that the generated code is correct,
+and will not raise runtime errors in the SMT engine. Remark that the
+\texttt{declare-datatypes} command include both the Action
+constructors from table \ref{table:BIPalgebra}, but also the constant action
+names from our example.
 
 \paragraph{Translating assignments into predicate terms}
-\TODO{Exerpt of the formalisation}
+\TODO{Only if we have it in the example...}
 
@@
 
-State-variable assignments are also treated as a part of the
-predicates when checking the satisfiability. % Here we need conduct some
-% translations,
-For each assignement in a $\Post$ predicate, such as $\{s_0 \leftarrow 1\}$ in section
-~\ref{section:op-semantics}, we translate it into an equation
-$s_0=1$. For several assignments of the same variable in the same state,
-we generate the disjunction of 
-these equations. Correspondingly, we generate a conjunction for the
-assignments from different variables.
+%% State-variable assignments are also treated as a part of the
+%% predicates when checking the satisfiability. % Here we need conduct some
+%% % translations,
+%% For each assignement in a $\Post$ predicate, such as $\{s_0 \leftarrow 1\}$ in section
+%% ~\ref{section:op-semantics}, we translate it into an equation
+%% $s_0=1$. For several assignments of the same variable in the same state,
+%% we generate the disjunction of 
+%% these equations. Correspondingly, we generate a conjunction for the
+%% assignments from different variables.
 
@@
 
-% We check the satisfiability of open transitions on the top level of
-% the pNet, treating these open transitions as the intermediate result
-% of the algorithm. After we get the intermediate results of open
-% transitions, we check them one by one.
-Here we declare first all the variables in the predicates, with their
-sorts.
-An example of syntax is::\\
-\centerline{$\OTvar{(declare-const\ |:ra:1:1|\ Action)}$}
-
-\noindent Then each term of the
-predicate is an assertion in Z3, as an example, in the former
-unsatisfiable result in Fig~\ref{schema:unsat-ot}, the contradiction is occurred in terms: \\
-\centerline{$\OTvar{(:ra:11:1=l)} \OTland \OTvar{(delta=:ra:11:1)}$}\\
-from which we generate the following two assertions:\\
-\centerline{$\OTvar{(assert\ (=\ |:ra:11:1|\ l))\ \ \ (assert\ (=\ delta\ |:ra:11:1|))}$}
-
-\noindent The predicate submitted to the Z3 also contains the
-assignments encodings.
-In the case of $ot_2$, it
-gives the assertion:\\
-\centerline{$\OTvar{assert (or (= var\_s0 0) (= var\_s0 01)))}$}
+In appendix \ref{appendix:mapsmt} we formaly define the translation of each
+open transition, including:
+- collect all variables in the transition, and declare them,
+- check well-formness and correct typing of expressions
+- translate the predicate into a conjunction of assertations
+- if present in the source state, translate the state-variable
+assignments into a disjunctive assertion.
+Here again, this translation ensures that no runtime error will occur
+when running the SMT engine.
+
+In Fig.~\ref{schema:smt-lib} you can see the decomposition of the
+predicate into a set of asserts, each encoding an elementary equality,
+inequality, or a guard. The final command in the translation is a
+\texttt{(check-sat)}, which result (sat or unsat) will be decoded by
+our algorithm.
 
 \subsection{Simplification of Predicates}
-\ERIC{: motivated, add refs, and an abstract presentation of stuff from pages 19-20}
+\ERIC{: motivated, add refs, and an abstract presentation of stuff
+  from pages 19-20. The following is NOT a good example, we should
+  rather use a pNet with at least 2 levels, to have real intermediate
+variables; here b0, b1, b2 are NOT intermediate variables... and the
+predicate simplification is using `some form of ``tautology checking''
+rather thanm rewritting.}
 
@@
 
-\TODO{Xudong: Update: we have 11 satisfiable OTs here}
-Our tool builds 30 open
-transitions, out of which 27 are detected unsatisfiable by Z3, we
-get only 3 results left; the resulting open automaton is shown in
-Fig. ~\ref{schema:lotos-result}, together with its open transitions.
+On this example, the tool builds 184 open
+transitions, out of which 173 are detected unsatisfiable by Z3, we
+get only 11 results left; the resulting open automaton is shown in
+Fig. ~\ref{schema:full-result}, together with its open transitions.
 
@@
 predicate.
-\TODO{missing some comments on this result OA}.
+
+Remark that only 3 global states out of the possible 6 are reachable
+here. \TODO{it would be good to express here maybe 2 properties of the
+  architecture, maybe one taken fromm the original study, and another
+  one involving the timer data (number of ticks ?)}
 
@@
  \end{figure}
-
-\begin{figure}[h]
-%  \centerline{\includegraphics[width=5cm]{XFIG/LOTOSresult}}
-  \TODO{Detaisl of some OTs of the FailureTimer}
-
-$\begin{array}{@{}r@{}l@{}}
-    ot_1  = &\openrule{\{0 \xrightarrow{l}_{C_1} 0\}, ~~\{\xrightarrow{hb_{1}}_P\}, ~~[s_0=0 \!\land\! hb_{1} \neq \delta(x) \!\land\! v_1=hb_{1}]}
-    {\ostate{00} \xrightarrow{v_1} \ostate{00}}\\
-  \end{array}$
-
-$\begin{array}{@{}r@{}l@{}}
-    ot_2  = &\openrule{\{0 \xrightarrow{\delta}_{C_1} 0, 0 \xrightarrow{acc(x)}_{C_2} 1\}, ~~\{\xrightarrow{hb_{2}}_P\}, ~~[s_0=0 \!\land\!
-hb_{2}=\delta(x) \!\land\!
-v_2=\underline{\delta(x)}], ~~\{s_0 \xleftarrow{} 1\}}
-    {\ostate{00} \xrightarrow{v_2} \ostate{01}}\\
-  \end{array}$
-
-\caption{The open automaton of the LOTOS formula}  \label{schema:lotos-result}
-\end{figure}
-
-%\subsubsection{Result of CCS example}
-%\QIN{
-%also can present all the possible behavior of that CCS formula with 16 open
-%transitions in Fig. ~\ref{schema:ccs-result}, here we omitted the details of open transitions. 
-%In this example, there are 32 more transitions detected unsatisfiable by Z3.
-%}
-%
-%\QIN{
-%Here we only show one of the result transitions. It presents the value-passing between $a.P$ and $b.Q$ and they are synchronized then
-%give out an silent action $\tau$, process $P$ and $Q$ should not work in this case.
-%}
-%
-%\begin{figure}[h]
-%  \centerline{\includegraphics[width=5cm]{XFIG/CCSresult}}
-%  
-%  $\begin{array}{@{}r@{}l@{}}
-%    ot_1  = &\openrule{\{0 \xrightarrow{a}_{C_1} 1, 0 \xrightarrow{b}_{C_2} 1\}, ~~a=!ch_{11}(v_{11}) \!\land\! b=?ch_{11}(v_{11}) \!\land\! a\neq l \!\land\! b\neq r\!\land\! v_1=\tau}
-%    {\ostate{00} \xrightarrow{v_1} \ostate{11}}\\
-%  \end{array}$
-%  
-%\caption{The open automaton of the CCS parallel formula}  \label{schema:ccs-result}
-%\end{figure}
-
-%% \QIN{
-%% To sum up, from the pNets encoding the formulas of given algebra, which inputed by the user, we can exactly construct
-%% the open automaton for them. 
-%% }
 
@@
                 $\texttt{true},\ \texttt{false}$&
-                $\land,\ \lor$
+                $\land,\ \lor,\ \neg,\ \implies$
                 \\\specialrule{0em}{1pt}{1pt} 
-		Action 			&  $\texttt{FUN}$ &
+		Action 			&  $texttt{FUN}$ &
                 \\\specialrule{0em}{1pt}{1pt}

### 2018-01-17 2017-Xudong-SMT/FM-2018-extended.tex
Add the transition rules for Pred and Assign.
On page 21. Section C.2.

@@
 
-\begin{lstlisting}
 Let Pres = <Sorts, Constrs, Ops> be the extended presentation
 and OT = <Leaves, Holes, Pred, Assign> an open transition.
-- compute the environment $\EEnv=\EEnv_{pnet,OT}$ collecting
-all variables used in OT
-- check that all pLTS labels (action, guard, assignement) in
+\begin{itemize}
+\item compute the environment $\EEnv=\EEnv_{pnet,OT}$ collecting
+all variables used in OT.
+\item check that all pLTS labels (action, guard, assignement) in
 the transition, the OT predicate, and the OT assignments are
-well-formed and well-typed
-- for each variable $v$ in $\EEnv$, construct:
-  define-const = TrPredicate ($\EEnv,v$)
-- turn the predicate into conjunctive normal form
-- for each conjunct $P_i$ in the predicate, construct:
-  assert = TrPredicate $(P_i)$
-\end{lstlisting}
+well-formed and well-typed.
+\item for each start global state $gs$ of the open transition, using $SVar(gs)$
+  get the state variables and their possible evaluations from all the state in $gs$.
+  Then use Ass(x) as the set of evaluations of state variable x.
+\item for each variable $v$ in $\EEnv$, construct:
+  define-const = TrPredicate ($\EEnv ,v$).
+%- turn the predicate into conjunctive normal form
+\item for each conjunct $P_i$ in the predicate, construct:
+  assert = TrPredicate $(P_i)$.
+\end{itemize}
 
@@
 
-\begin{tabular}{p{5cm}p{5cm}p{2.5cm}}
+\begin{tabular}{p{5cm}p{7cm}}
 		\hline\specialrule{0em}{3pt}{3pt}
-		\multicolumn{2}{l}{Variables}
-
-		& 			\\\specialrule{0em}{1pt}{1pt}
+		\multicolumn{2}{l}{Variables:}
+		\\
 		$\dfrac{\EEnv \vdash x:A }
-                       {x \translate \texttt{(declare-const x A)}}$
-
-		&&       		\\\specialrule{0em}{1pt}{1pt}
-		\multicolumn{2}{l}{Predicate conjunct: }
-
-		& 			\\\specialrule{0em}{1pt}{1pt}
-		$\dfrac{}
-                       {P_i \translate \texttt{(assert ... }}$
-
-		&&       		\\\specialrule{0em}{1pt}{1pt}
-		\multicolumn{3}{p{12cm}}{To be completed with translation of
-                expressions, including special cases for EQ, NOT\_EQ,
-                and FUN }
-
-		 			\\\specialrule{0em}{1pt}{1pt}
+                       {x \translate \texttt{(declare-const x A)}}$&
+		\\\specialrule{0em}{3pt}{3pt}
+		Open transition: 
+		\\
+		$\dfrac{Pred \translate lst_1~~Ass \translate lst_2}{ot(Pred, Assign) \translate lst_1 lst_2}$
+		\\\specialrule{0em}{3pt}{3pt}
+		Predicate: & Predicate conjunct:
+		\\
+		$\dfrac{Pred = \bigwedge\limits_{k\in K}P_k}{Pred \translate \texttt{map} \translate P_k}$&	$\dfrac{P_k = op(args)}{P_k \translate \texttt{(assert (op map}\longrightarrow \texttt{args))}}$
+		\\\specialrule{0em}{3pt}{3pt}
+		$\dfrac{\EEnv \vdash x:A }{Var(x) \longrightarrow \texttt{x}}$
+		\\\specialrule{0em}{3pt}{3pt}
+		$\dfrac{arg = op'(args)~~op'\in Constr~~arity(op') = 0}{op' \longrightarrow name(op')}$
+		\\\specialrule{0em}{3pt}{3pt}
+		$\dfrac{arg = op'(args)~~op'\in Constr~~arity(op')\neq 0}{op' \longrightarrow \texttt{(}name(op')~~map\longrightarrow args\texttt{)}}$
+		\\\specialrule{0em}{3pt}{3pt}
+		$\dfrac{arg = op'(args)~~op'\in Ops}{op' \longrightarrow \texttt{(}name(op')~~map\longrightarrow args\texttt{)}}$
+		\\\specialrule{0em}{3pt}{3pt}
+		Assignment: 
+		\\
+		$\dfrac{Assign = \bigwedge\limits_{k\in K}(x_k, a_k)~~x_k\in SVar(gs)~~a_k = Ass(x_k)}{Assign \translate \texttt{map} \translate (x_k, a_k)}$
+		\\\specialrule{0em}{3pt}{3pt}		
+		$\dfrac{a_k = e_1,...,e_n}{(x_k, a_k) \translate \texttt{(assert (or (= }x_k\texttt{ map} \longrightarrow e_1\texttt{)}\texttt{...(= }x_k\texttt{ map} \longrightarrow e_n\texttt{)}  \texttt{))}}$
+		\\\\\specialrule{0em}{1pt}{1pt}
 	        \hline

### 2018-01-17 2017-Xudong-SMT/FM-2018-extended.tex
head of appendix

--- 2018-01-17 2017-Xudong-SMT/FM-2018-extended.tex
@@
 
-\TODO{To be reduced, moving more material to the appendix}
-
 This section introduces pNets and the notations we will use in
@@
 
-\subsection{Simplification of Predicates}
-\ERIC{: motivated, add refs, and an abstract presentation of stuff
-  from pages 19-20. The following is NOT a good example, we should
-  rather use a pNet with at least 2 levels, to have real intermediate
-variables; here b0, b1, b2 are NOT intermediate variables... and the
-predicate simplification is using `some form of ``tautology checking''
-rather thanm rewritting.}
-
-Before:
-  	\begin{mathpar}
-	\inferrule*[myfraction=\reddottedrule]
-	{\{s0~{\xrightarrow{fail(true)}} ~s1, t0~{\xrightarrow{start(true)}} ~t1\}
-	  \{\xrightarrow{hb}\},\\
-\qquad b1=true \land b2=true \land hb=fail(b0) \land b1=b2 \land (b1\cup b2
-\implies b0) \land v=\underline{fail}, \{t := 4\}
-        }
-	{<s0,t0> \xrightarrow {v} <s1,t1>}
-	\end{mathpar}
-
-After:
-          	\begin{mathpar}
-	\inferrule*[myfraction=\reddottedrule]
-	{\{s0~{\xrightarrow{fail(true)}} ~s1, t0~{\xrightarrow{start(true)}} ~t1\}
-	  \{\xrightarrow{hb}\}, hb=fail(true) \land v=\underline{fail}, \{t := 4\}
-        }
-	{<s0,t0> \xrightarrow {v} <s1,t1>}
-	\end{mathpar}
-
 \subsection{Result of the running example}
@@
 \appendix
-\section{Appendix}
+%\section{Appendix}
 The following appendices are included for the convenience of reviewers.
@@
 extended version containing all technical detials, proofs, and more examples.
+
+These are organized in th efollowing way:
+
+\begin{enumerate}
+\item[A] pNet semantic rules
+\item[B] Variable managment
+\item[C] Translation to SMTlib input language
+\item[D] Well-formness and typing of expressions
+\item[E]
+
+\end{enumerate}
 
@@
 
-\section{More details on the generation algorithm}
-
-\subsection{Variable managment}
-The variables in each synchronisation vector are considered local: for a given pNet expression, we must have fresh local variables for each occurrence of a vector (= each time we instantiate rule Tr2).
-Similarly the state variables of each copy of a given pLTS in the system, must be distinct, and those created for each application of Tr2 have to be fresh and all distinct.
-This will be implemented within the open-automaton generation algorithm, e.g.
-using name generation using a global counter as a suffix.
-
-\subsection{Translation to SMTlib input language}
+% \section{More details on the generation algorithm}
+
+\section{Variable managment}
+The variables in each synchronisation vector are considered local: for
+a given pNet expression, we must have fresh local variables for each
+occurrence of a vector (= each time we instantiate rule
+Tr2). Similarly the state variables of each copy of a given pLTS in
+the system, must be distinct, and those created for each application
+of Tr2 have to be fresh and all distinct. This will be implemented
+within the open-automaton generation algorithm, e.g. using name
+generation using a global counter as a suffix.
+\TODO{add structure of generated names}
+
+\section{Translation to SMTlib input language}
 In order to submit satisfiability problems to Z3 (for the predicates
@@
 
+\subsection{Definition of an algebra presentation}
 We have a minimal, predefined algebra presentation for all pNets, including
@@
                 \\\specialrule{0em}{1pt}{1pt} 
-		Action 			&  $texttt{FUN}$ &
+		Action 			&  $\texttt{FUN}$ &
                 \\\specialrule{0em}{1pt}{1pt}
@@
                 \textsl{for any sort} & & $=,\ \ne$
+		\\\hline
+	\end{tabular}
+\end{table}
+
+\begin{table}\caption{\label{table:BIPalgebra}\leftline{Additional
+      operator for the BIP algebra}}
+	\begin{tabular}{p{3cm}p{3cm}p{6cm}}
+		\hline\specialrule{0em}{1pt}{1pt}
+		Sort & Constructors & Other Operators
+                \\\hline\specialrule{0em}{1pt}{1pt} 
+		Action 			&  $\texttt{FUN\_Action\_Bool}$ &
 		\\\hline
@@
 
-Then in pNet API these operators or constants (seemed as non-parameter operators) can be declared as:
-\begin{lstlisting}[basicstyle=\footnotesize\ttfamily, language=java, frame=single]
+\begin{table}\caption{\label{table:BIPalgebra}\leftline{Additional
+      sorts and operators for the CCS algebra}}
+	\begin{tabular}{p{3cm}p{3cm}p{6cm}}
+		\hline\specialrule{0em}{1pt}{1pt}
+		Sort & Constructors & Other Operators
+                \\\specialrule{0em}{1pt}{1pt}
+		\hline\specialrule{0em}{3pt}{3pt}
+		Channel, Data    			&
+                $\emptyset$&
+                $\emptyset$
+                \\\specialrule{0em}{1pt}{1pt} 
+		Action 			&  $\texttt{Emit(c,v)},\texttt{Receive(c,v)},\texttt{Tau}$ &
+		\\\hline
+	\end{tabular}
+\end{table}
+
+Then in pNet API these operators or constants can be declared as:
+\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
 AlgebraSort Action = new AlgebraSortImpl("Action");
@@
 
-\paragraph{Expressions}
-Once an algebra presentation is defined, we can construct expressions
-of the term algebra, using variables and operators:
-
-\begin{definition}
-  Let $\mathcal{V}$ be a set of variables. The Term Algebra
-  $\Sigma_{\mathcal{P},\mathcal{V}}$ is the set of:
-  \begin{itemize}
-  \item variables $x \in \mathcal{V}$
-  \item terms (or expressions) $op (arg_1, ... , arg_n)$ with $op$ an operator in
-  $\mathcal{P}$ of arity $n$, and each $arg_i$ an expression.
-  \end{itemize} 
-\end{definition}
-
-\paragraph{Constants and variables in pNets and in open transitions}
+%\subsection{Constants and variables in pNets and in open transitions}
+\subsection{Extended presentation, and Environment}
 
@@
 
-\paragraph{Well-formed and well-typed expressions}
+\section{Well-formness and typing of expressions}
 
@@
 expressions respect the arity of operators), and typing rules.
-\TODO{Eric: refer in the appendix header}
+%\TODO{Eric: refer in the appendix header}
 
@@
 
-\subsubsection{Map to SMT-LIB language}
+\section{Map to SMT-LIB language}
 The pNet elements, as defined above, can be full translated into
@@
 In this section we shall define separately the translation of the
-(extended) algebra presentation for one pNet (so it will be fixed for
-the study of one use-case); and the translation of each predicate in
-the context of an open-transition of this pNet.
+extended algebra presentation for one pNet (so it will be common for
+the study of all OTs of one use-case); and the translation of each
+predicate (of an open-transition) of this pNet.
 
@@
 \subsection{Simplification of Predicates}
-\TODO{[Eric]: Motivate, and refs  -- reduce the section here to approx
-  half a page (from the next two pages...)}
+\subsection{Simplification of Predicates}
+\ERIC{: motivated, add refs, and an abstract presentation of stuff
+  from pages 19-20. The following is NOT a good example, we should
+  rather use a pNet with at least 2 levels, to have real intermediate
+variables; here b0, b1, b2 are NOT intermediate variables... and the
+predicate simplification is using `some form of ``tautology checking''
+rather thanm rewritting.}
+
+Before:
+  	\begin{mathpar}
+	\inferrule*[myfraction=\reddottedrule]
+	{\{s0~{\xrightarrow{fail(true)}} ~s1, t0~{\xrightarrow{start(true)}} ~t1\}
+	  \{\xrightarrow{hb}\},\\
+\qquad b1=true \land b2=true \land hb=fail(b0) \land b1=b2 \land (b1\cup b2
+\implies b0) \land v=\underline{fail}, \{t := 4\}
+        }
+	{<s0,t0> \xrightarrow {v} <s1,t1>}
+	\end{mathpar}
+
+After:
+          	\begin{mathpar}
+	\inferrule*[myfraction=\reddottedrule]
+	{\{s0~{\xrightarrow{fail(true)}} ~s1, t0~{\xrightarrow{start(true)}} ~t1\}
+	  \{\xrightarrow{hb}\}, hb=fail(true) \land v=\underline{fail}, \{t := 4\}
+        }
+	{<s0,t0> \xrightarrow {v} <s1,t1>}
+	\end{mathpar}
 

### 2018-01-17 2017-Xudong-SMT/FM-2018-extended.tex
appendix structure

@@
 
+To have some practical interest, it is important to know when this
+algorithm terminates. The following theorem shows that an open-pNet
+with finite synchronization sets, finitely many leaves and
+holes, and each pLTS at leaves having a finite number of states and
+(symbolic) transitions, has a finite automaton. The proof can be found
+in \cite{henrio:Forte2016}.
+
+\begin{theorem}[Finiteness of open-automata.]\\
+Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
+  J}$, if the sets $L$ and $J$ are finite, if the synchronization vectors of all pNets 
+  included in  $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ 
+  are finite, and if
+$\forall i \in L.\, finite{(states(pLTS_i))} \text{ and } pLTS_i$
+has a finite number of state variables, then Algorithm 1 terminates
+and produces an open automaton 
+$\mathcal{T}$ with finitely many states and transitions.
+
+Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in
+    K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
+  J}$,
+build its semantics as in algorithm 1.
+
+We have:
+
+$$ finite{(L)} \land finite{(J)} \land \forall i \in L finite{(\{s_i\})}
+  \to finite{(\mathcal{T})}$$
+\end{theorem}
+
 % \section{More details on the generation algorithm}
@@
 generation using a global counter as a suffix.
-\TODO{add structure of generated names}
+
+\paragraph{Fresh variables}
+Application of the semantic rules require generating a lot of fresh
+names, for different kind of variables. We could use a global name
+generator to guarantee unicity, but 
+at the same time, we also hope them still
+readable. Here we rename the variables with a regular format using the fresh function.
+More precisely, the fresh function generates a new name adding a
+suffix after the original name. The suffix contains three parts
+combined by a colon.
+
+\begin{definition}[Fresh variable]\label{fresh-variable}
+The format of \emph{fresh variable} (renaming) is defined as:
+``$\emph{prefix : tree\ index\ :\ counter}$''.
+\begin{itemize}
+   \item[$\bullet$] $prefix$ identifies the kind of the
+     variable. current kinds are: sva (SV action), ra (result action), hb (hole behavior).
+   \item[$\bullet$] $tree\ index$ is the index of the node containing the variable in the tree-like structure of the pNet.
+   \item[$\bullet$] $counter$ is the current value of the corresponding counter.
+\end{itemize}
+\end{definition}
+
+%\TODO{Option: Add the process and the vector ids ?}
+
+%$Prefix$ avoids the confusion between variables from different structures with the same name by attaching the type of the structure.
+$Tree\ index$ is given to every node of the pNets to mention which node the variable belongs to as pNets has a tree-like structure.
+To each node, the tree index is always a number sequence of the tree index of its higher level and the index of the node in this level at the last.
+$A\ set\ of\ counters$ is used to count the current times the SV, Hole, subnet invoked, or the number of possible OT generated to provide an identity.
+
+For example, in the running example, the first possible behavior of
+the hole, it doesn't have a name, only have the prefix ``hb''. The
+hole is the second subnets of the root node so its ``tree index'' is
+``12''. The fresh variable name is ``$\OTvar{:hb:12:1}$''.
 
@@
 
+% \TODO{This is incomplete... Xudong: Conjunctive normal form, translation function for boolean expressions, + assignments}
+
 \noindent
-\TODO{This is incomplete... Xudong: Conjunctive normal form, translation function for boolean expressions, + assignments}
-
 \begin{tabular}{p{5cm}p{7cm}}
@@
 
-\paragraph{Presentation of algebra}
-
-\TODO{Improve this, inserting the main definition from the ``Checker'' document}
-%% Open pNet framework provides us
-%% with a model able to express the semantics of many different algebras
-%% or languages. In particular,
-As seen in section
-\ref{section:pnets}, the \emph{term algebra} used to express the
-action expressions and data parameters is left open in
-the pNet definition.
-
-So, for a given language, we now need to specify its data and action
-domains, giving them an abstract syntax (sorts, constructors, operators,
-and predicates). We call this a \emph{Presentation}.
-We also define a concrete syntax, that will be used for
-pretty-printing, but also for translating the presentation, and the
-predicates, into Z3 syntax (see the ``declare-datatypes'' statement in
-Fig~\ref{schema:smt-lib}).
-
-An algebra presentation contains:
-
-\begin{itemize}
-	\item Sorts: Constants sets of the algebra or types of the data
-          and actions (integer and boolean sort are implicitly
-          declared).  There \emph{must} be one sort for actions, and
-          eventually others for the types of data
-          parameters. In the LOTOS example, 
-          we have the $Action$ sort: $\OTvar{Action = } \{ l, \delta,
-          r, p, q, acc \} .$
-
-	\item Operators:
-          %Operators used to construct action expressions; they are
-          constructors and predicates for data and action sorts. For
-          instance, in our LOTOS example, we
-          have a generic action constructor ``$ACT$'', taking as
-          argument an action litteral and a data parameter, declared as:
-          $\OTvar{ACT:}\OTvar{< Action, Data >} \rightarrow \OTvar{Action.}$, 
-        \item Constants: The satisfiability solver need to know which
-          actions in the pLTS behaviors are constants (like the $l$, $\delta$, 
-          $r$ of the controllers in running example). 
-          For a given pNet system, the sort $Action$ will include all
-          these constants.
-\end{itemize}
-
-\paragraph{Interaction with Z3}
-%\TODO{1. example input of Z3 in SMT-LIB.[DONE] 2. software architecture.[DONE]}
-%There are several ways to interact with the Z3 solver. 
-%It is possible to use Z3 interactively using the SMT-LIB
-%(Python-based) language. 
-From inside our algorithm code, we submit satisfiability requests to
-Z3 using its JAVA API. Here for readability, we
-show the Z3 code using its SMT-LIB input language. As an
-example in
-Fig~\ref{schema:smt-lib}, we show the input for checking the
-transition of Fig.~\ref{schema:unsat-ot}. It contains the declaration
-of the LOTOS action algebra types 
-and constructors, then the declaration of variables, and finally the
-predicate to be checked, encoded as a set of assertions.
-%% Generally, some $datatypes$ are declared to input the sorts, while here
-%% we only declare one $datatypes$ named $Action$ to involve all the
-%% constant actions. Then we input the predicate of this open transition
-%% in two parts: the variables contained in the predicate are declared
-%% first, then the terms of predicate are inputed as $assertions$ one by
-%% one. 
-The result "unsat" in the output is just what we expected.
-
-%\TODO{edit the figure to make it smaller in height [DONE]}
-
-%We present the architecture of the interaction with Z3 in
-%Fig~\ref{schema:interaction}.
-%For each OT generated at the toplevel of a pNet, the predicate must be
-%submitted for satisfiability check to Z3. For that we need to
-%translate into Z3 (Java-API) syntax, both the elements of the action
-%algebra, and the predicates itself, including the encoding of the
-%variable assignments (the Post part).
-%
-%The $presentation$ of the action algebra
-%is declared at the beginning of the algorithm as the $sorts$ and the
-%$operators$ will be used throughout the whole algorithm. It is
-%translated into $datatypes$ and $functions$ then submitted to the Z3
-%at the same time. Each candidate predicate will then be translated
-%into $assertions$ before submitted to Z3 after the algorithm
-%computing out all the possible open transitions, they act as
-%intermediate results there. Together with the $datatypes$ and
-%$functions$, the $assertions$ are used to check the satisfiability of
-%the predicate in Z3.
-
-To build the input submitted to Z3 for each OT,
-we translate the algebra $presentation$, the predicates and the
-variable assignments (the Post part) into Z3 (Java-API) syntax.
-% The $presentation$ and the predicates are translated separately.
-
-\paragraph{Translation of Action algebra presentation}
-\TODO{Exerpt of the formalisation}
-The $datatypes$ are declared according to the $sorts$ the users
-declared in the $presentation$. If the return type of the $functions$
-is one of the $datatypes$, we add this $function$ to the $datatypes$ declaration.
-So when we declare the operator ACT we illustrated in section 4.1, it
-will be just declared together with the constants like :\\
-\centerline{$\OTvar{(ACT\ (action3\ Action)(data\ Int))}$}
-
-The $functions$ can also be declared independently, it usually applies to functions returning integer or boolean, in the format like:\\
-\centerline{$\OTvar{(declare\text{-}fun\ MAX\ (Int\ Int)\ Int)}$}
-
-%Although in Fig~\ref{schema:smt-lib} we have not declared $functions$ outside of $datatypes$, there still exists $functions$ declared independently.
-The input and output types of the $function$ are also determined by the construct of the  $operators$ in the presentation.
-For example, we define a new operator to present the equation between two actions in LOTOS example $\text{EQUAL}$ in the format likes:
-%
-%\[EQUAL: \quad < Action , Action > \rightarrow Bool .\]
-%
-%It will be translated into the Z3 statement: 
-%
-%\[\text{(declare-fun\ EQUAL\ (Action\ Action)\ Bool) .}\]
-
 \paragraph{Translating assignments into predicate terms}
-\TODO{Exerpt of the formalisation}
-
-%The assignments are also taken into account when checking the
-%satisfiability of the open transitions as they represent the value of
-%the variables involved in an OT. In order to do that, we employs a
-%translation from assignments into term of predicates. The assignments
-%required to be translated are only those belong to the variables
-%contain in the start states of the open transitions. The assignments
-%are represented as equations between the variables and the expressions
-%on the right side of assignment. For the assignments of the same
-%variable, we do not figure out which state is the precursor of current
-%state, we keep all these possible equations instead, and generate the
-%disjunction of these equations. The state could always move to the
-%target state if there exists one of the values of its variable
-%satisfies the guard.
-%%\TODO{It won't matter the variable of the next state
-%%except that the right hand side expression contain its variables. This
-%%is a problem left to be solved in our future work. WHICH PROBLEM ?}
-%After that, for the assignments of the different variables, we generate a conjunction of them. This way we obtain a new term of the predicate involving assignments of the variables.
 
@@
 
-\paragraph{Checking satisfiability}
-
-% We check the satisfiability of open transitions on the top level of
-% the pNet, treating these open transitions as the intermediate result
-% of the algorithm. After we get the intermediate results of open
-% transitions, we check them one by one.
-Here we declare first all the variables in the predicates, with their
-sorts.
-An example of syntax is::\\
-\centerline{$\OTvar{(declare-const\ |:ra:1:1|\ Action)}$}
-
-\noindent Then each term of the
-predicate is an assertion in Z3, as an example, in the former
-unsatisfiable result in Fig~\ref{schema:unsat-ot}, the contradiction is occurred in terms: \\
-\centerline{$\OTvar{(:ra:11:1=l)} \OTland \OTvar{(delta=:ra:11:1)}$}\\
-from which we generate the following two assertions:\\
-\centerline{$\OTvar{(assert\ (=\ |:ra:11:1|\ l))\ \ \ (assert\ (=\ delta\ |:ra:11:1|))}$}
-
-\noindent The predicate submitted to the Z3 also contains the
-assignments encodings.
-In the case of $ot_2$, it
-gives the assertion:\\
-\centerline{$\OTvar{assert (or (= var\_s0 0) (= var\_s0 01)))}$}
+%% \paragraph{Checking satisfiability}
+
+%% % We check the satisfiability of open transitions on the top level of
+%% % the pNet, treating these open transitions as the intermediate result
+%% % of the algorithm. After we get the intermediate results of open
+%% % transitions, we check them one by one.
+%% Here we declare first all the variables in the predicates, with their
+%% sorts.
+%% An example of syntax is::\\
+%% \centerline{$\OTvar{(declare-const\ |:ra:1:1|\ Action)}$}
+
+%% \noindent Then each term of the
+%% predicate is an assertion in Z3, as an example, in the former
+%% unsatisfiable result in Fig~\ref{schema:unsat-ot}, the contradiction is occurred in terms: \\
+%% \centerline{$\OTvar{(:ra:11:1=l)} \OTland \OTvar{(delta=:ra:11:1)}$}\\
+%% from which we generate the following two assertions:\\
+%% \centerline{$\OTvar{(assert\ (=\ |:ra:11:1|\ l))\ \ \ (assert\ (=\ delta\ |:ra:11:1|))}$}
+
+%% \noindent The predicate submitted to the Z3 also contains the
+%% assignments encodings.
+%% In the case of $ot_2$, it
+%% gives the assertion:\\
+%% \centerline{$\OTvar{assert (or (= var\_s0 0) (= var\_s0 01)))}$}
 
 \subsection{Simplification of Predicates}
-\subsection{Simplification of Predicates}
+\TODO{I keep it here for now, but I think we shall not include it in
+  the FM submission, this section is not mature enough}
+
 \ERIC{: motivated, add refs, and an abstract presentation of stuff
@@
 predicate simplification is using `some form of ``tautology checking''
-rather thanm rewritting.}
+rather than rewritting.}
 
@@
 
-%\subsubsection{Result of CCS example}
-%\QIN{
-%also can present all the possible behavior of that CCS formula with 16 open
-%transitions in Fig. ~\ref{schema:ccs-result}, here we omitted the details of open transitions. 
-%In this example, there are 32 more transitions detected unsatisfiable by Z3.
-%}
-%
-%\QIN{
-%Here we only show one of the result transitions. It presents the value-passing between $a.P$ and $b.Q$ and they are synchronized then
-%give out an silent action $\tau$, process $P$ and $Q$ should not work in this case.
-%}
-%
-%\begin{figure}[h]
-%  \centerline{\includegraphics[width=5cm]{XFIG/CCSresult}}
-%  
-%  $\begin{array}{@{}r@{}l@{}}
-%    ot_1  = &\openrule{\{0 \xrightarrow{a}_{C_1} 1, 0 \xrightarrow{b}_{C_2} 1\}, ~~a=!ch_{11}(v_{11}) \!\land\! b=?ch_{11}(v_{11}) \!\land\! a\neq l \!\land\! b\neq r\!\land\! v_1=\tau}
-%    {\ostate{00} \xrightarrow{v_1} \ostate{11}}\\
-%  \end{array}$
-%  
-%\caption{The open automaton of the CCS parallel formula}  \label{schema:ccs-result}
-%\end{figure}
-
-%% \QIN{
-%% To sum up, from the pNets encoding the formulas of given algebra, which inputed by the user, we can exactly construct
-%% the open automaton for them. 
-%% }
-
-% \newpage
-%\appendix
-
-\section{More details on the generation algorithm}
-
-%\paragraph{Fresh variables management.}
-
-% This will be implemented within the open-automaton generation algorithm,
-% e.g. using name generation using a global counter as a suffix.
-
-% \TODO{To be move  by Xudong}
-
-%\subsection{Presentation of algebra}
-%One of the important goal of the Open pNet framework is to provide us
-%with a model able to express the semantics of many different algebras
-%or languages. In particular, as we have seen in section
-%\ref{section:pnets}, the \emph{term algebra} used to express the
-%action expressions and the data in their parameters is left open in
-%the pNet formalization.
-%
-%So, for a given language, we now need to specify its data and action
-%domains, giving them an abstract syntax (sorts, constructors, operators,
-%and predicates). We call this a \emph{Presentation}.
-%We also define a concrete syntax, that will be used for
-%pretty-printing, but also for translating the presentation, and the
-%predicates, into Z3 syntax (we shall detail this translation in
-%section \ref{section:pruning}).
-%
-%An algebra presentation contains:
-%\begin{itemize}
-%	\item Sorts: Constants sets of the algebra or types of the data
-%          and actions. In every presentation, sorts for integer and
-%          boolean are implicitly declared.  There \emph{must} be one sort for actions, and eventually 
-%several others for the types of data parameters. In the LOTOS example,
-%we have the $Action$ sort: $\OTvar{Action = } \{ l, \delta, r, p, q, acc \} .$
-%
-%	\item Operators: Operators used to construct action
-%          expressions (including their data parameters); they are
-%          constructors of data and action sorts, but also predicates
-%          over these objects. For instance, in our LOTOS example, we
-%          could have two constructor functions ``$DELTA$'' and ``$ACC$''
-%          to construct the action expression $\delta(x)$ and $acc(x)$, declared as:
-%          $\OTvar{DELTA:}\OTvar{< Data >} \rightarrow \OTvar{Action .}$
-%        \item Constants: The satisfiability solver need to know which
-%          actions in the pLTS behaviors are constants (like the $l$, $\delta$, 
-%          $r$ of the controllers in running example). 
-%          For a given pNet system, a sort $Action$ will include all
-%          these constants.
-%\end{itemize}
-
-%We need introduce operators for building expressions, of both action
-%and data sorts, when encoding the 
-%algebra into pNets. So that is needed to know about the input and
-%output of the operators used in the expressions from those
-%algebra. The input and output should belong to the sorts of the
-%pNet. When there are $k$ sorts in this pNet, the structure of a
-%$n$-ary operator is vector as $< Sort_{i_1}, ... , Sort_{i_n} >
-%\rightarrow Sort_j , i_1 , ... , i_n, j \in [0..k] $.
-%% We  introduce operators for building expressions, either action
-%% expressions or predicate terms, when encoding the algebra into
-%% pNets. The operators here are treated as functions, with the sorts of
-%% the pNet acting as the types of their input and output. 
-%% For instance, in our LOTOS running example, we use a function ``$ACT$'' action to construct the action expression $\delta(x)$ and $acc(x)$.
-We can define the operator as a binary operator with the format like:
-
-%%  \[\OTvar{ACT:}\OTvar{< Action, Int >} \rightarrow \OTvar{Action .} \]
-
-%\paragraph{Implementation of the expression meta-model}
-% \TODO{maybe we could remove this paragraph (and the figure)}
-%The VerCors platform uses Ecore and EMF to define the structure of
-%both pNets and actions algebras. There exists a predefined set of
-%action and data expressions classes, including boolean, integer and
-%action expressions, with predefined variables, literal (constants),
-%and operators. Operators can be categorized into unary, binary and
-%N-ary operators.
-%The original version of VerCors did not allow to extend these classes,
-%we have modified its architecture so that a user can extend them,
-%defining more elements for his specific algebra.
-%
-%In Fig~\ref{schema:expression-pnets}, we show the Expression class we
-%improved, including extensions for CCS and LOTOS.
-%
-%\begin{figure}[t]
-%  \includegraphics[width=\linewidth]{XFIG/Expression}
-%  \caption{The architecture of Expression class}  \label{schema:expression-pnets}
-%\end{figure}
-
-%\TODO{give an example of user-defined sorts/operators, and tell that
-%  you will give it's translation into Z3 in section 5.4}
-
-% \TODO{To be move / replace by Xudong}
-
-%\subsection{Computing and using open automata}
-%In this section we present an algorithm to construct the open
-%automaton representing the behavior of an open pNet, and show
-%under which conditions this automaton is finite.
-%
-%\begin{alg}[behavioral semantics of open pNets: Sketch]
-%This is a standard residual algorithm over a set of open-automaton
-%states, but where transitions are open transitions
-%constructively ``proven'' by deduction trees.
-%
-%1) Start with a set of unexplored states containing the initial state
-%of the automaton, and an empty set of explored states.
-%
-%2) While there are unexplored states:
-%
-%2a) pick one state from the unexplored set and add it to the explored
-%set. From this state
-%build all possible deduction trees by application of the structural
-%rules Tr1 and Tr2, using all applicable combinations
-%of synchronization vectors.
-%
-%2b) For each deduction trees, extract the resulting
-%open-transition.
-%Its predicate is checked (using Z3) for  satisfiability. If it is
-%unsatisfiable, the resulting OT is discarded. This will minimize the
-%number of resulting transitions. 
-%
-%2c) For each open-transition,  add the transition in the outgoing transitions of
-%the current state, and add the
-%resulting state in the unexplored set if it is not already in the
-%explored set.
-%
-%3) Finally a reachability check could potentially
-%prune the state space.
-%
-%\end{alg}
-
-%% \TODO{ERIC: after we move / replace Algoriithm 1, this will not make sense any longer. I will replace it with a more informal paragraph, in section 5}
-
-%% To have some practical interest, it is important to know when this
-%% algorithm terminates. The following theorem shows that an open-pNet
-%% with finite synchronization sets, finitely many leaves and
-%% holes, and each pLTS at leaves having a finite number of states and
-%% (symbolic) transitions, has a finite automaton. The proof can be found
-%% in \cite{henrio:Forte2016}.
-
-%% \begin{theorem}[Finiteness of open-automata.]\\
-%% Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
-%%   J}$, if the sets $L$ and $J$ are finite, if the synchronization vectors of all pNets 
-%%   included in  $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ 
-%%   are finite, and if
-%% $\forall i \in L.\, finite{(states(pLTS_i))} \text{ and } pLTS_i$
-%% has a finite number of state variables, then Algorithm 1 terminates
-%% and produces an open automaton 
-%% $\mathcal{T}$ with finitely many states and transitions.
-
-% Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in
-%     K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
-%   J}$,
-% build its semantics as in algorithm 1.
-
-% We have:
-
-% $$ finite{(L)} \land finite{(J)} \land \forall i \in L finite{(\{s_i\})}
-%   \to finite{(\mathcal{T})}$$
-% \end{theorem}
-
-\subsection{Algebra specification}
-\subsection{Term algebra: type system and static semantics}
-\subsection{Fresh variables}
-
-%The variables in each synchronization vector are considered local, so
-%does the variables of an open transition such as its hole behaviors
-%and its result action. So we want rename the variables to make them
-%unique on every occurrence of a vector. Similarly, the name given to
-%the hole behaviors for each hole or the result action for each open
-%transition must be distinct. At the same time, we also hope them still
-%readable. Here we rename the variables with a regular format using the fresh function.
-
-Application of the semantic rules require generating a lot of fresh
-names, for different kind of variables. We could use a global name
-generator to guarantee unicity, but 
-at the same time, we also hope them still
-readable. Here we rename the variables with a regular format using the fresh function.
-More precisely, the fresh function generates a new name adding a
-suffix after the original name. The suffix contains three parts
-combined by a colon.
-
-\begin{definition}[Fresh variable]\label{fresh-variable}
-The format of \emph{fresh variable} (renaming) is defined as:
-``$\emph{prefix : tree\ index\ :\ counter}$''.
-\begin{itemize}
-   \item[$\bullet$] $prefix$ identifies the kind of the
-     variable. current kinds are: sva (SV action), ra (result action), hb (hole behavior).
-   \item[$\bullet$] $tree\ index$ is the index of the node containing the variable in the tree-like structure of the pNet.
-   \item[$\bullet$] $counter$ is the current value of the corresponding counter.
-\end{itemize}
-\end{definition}
-
-%\TODO{Option: Add the process and the vector ids ?}
-
-%$Prefix$ avoids the confusion between variables from different structures with the same name by attaching the type of the structure.
-$Tree\ index$ is given to every node of the pNets to mention which node the variable belongs to as pNets has a tree-like structure.
-To each node, the tree index is always a number sequence of the tree index of its higher level and the index of the node in this level at the last.
-$A\ set\ of\ counters$ is used to count the current times the SV, Hole, subnet invoked, or the number of possible OT generated to provide an identity.
-
-For example, in the running example, the first possible behavior of
-the hole, it doesn't have a name, only have the prefix ``hb''. The
-hole is the second subnets of the root node so its ``tree index'' is
-``12''. The fresh variable name is ``$\OTvar{:hb:12:1}$''. 
-\subsection{Variable managment}
-\subsection{Filtering the behaviour combinations}
-\subsection{Translation to SMTlib input language}
-\subsection{Elimination of intermediate variables}
-
 \section{Full examples}
-\TODO{May be we use two architecture examples here, a simpler one,
-  before the Failure Timer ?}
-\subsection{A very simple architecture}
+
 \subsection{Full input for the FailureTimer architecture}
@@
 
+\TODO{Not yet !}
+
 \end{document}

### 2018-01-17 2017-Xudong-SMT/FM-2018-extended.tex
Added the presentation of BIP, architectures and Failure Monitor, except for connectors

--- 2018-01-17 2017-Xudong-SMT/FM-2018-extended.tex
@@
 
+\input{XFIG/macros.tex}         % Definitions of macros used in XFig figures
+
 \def\AlgT{\mathcal{T}}
@@
 \def\AlgI{\mathcal{I}}
+
+\newcommand{\mdash}{---}
+\newcommand{\ndash}{--}
+\newcommand{\cf}[1][\ ]{cf.#1}
+\newcommand{\ie}[1][\ ]{i.e.#1}
+\newcommand{\etc}[1][\ ]{etc.#1}
+\newcommand{\eg}[1][\ ]{e.g.#1}
+\newcommand{\wrt}[1][\ ]{w.r.t.#1}
+
+\newcommand{\goesto}[2][]{\ensuremath{\xrightarrow[#1]{#2}}}
+\newcommand{\true}{\ensuremath{\mathit{true}}}
 
@@
 %\newcommand\openrule[2]{\inferrule*{#1}{#2}}
+
+%% SB: Moved the macro definitions from XFIG/figtex2eps-preamble.tex
+%%     to XFIG/macros.tex and added a com and to input this latter one
+%%     into the paper source (above in this file).
 %\newcommand\ostate[1]{\triangleleft{\;#1\;}\triangleright}
-\newcommand\ostate[1]{\triangleleft{#1}\triangleright}
+%\newcommand\ostate[1]{\triangleleft{#1}\triangleright}
 \newcommand{\sm}[1]{\mbox{\boldmath\small #1}}
@@
 
+\TODO{To be reduced, moving more material to the appendix}
+
 This section introduces pNets and the notations we will use in
@@
 
-\section{BIP architectures, and their encodings into pNets}
+\section{Running example}
+\label{section:FailureTimerMax}
 \label{section:BIParchitectures}
@@
 
-\TODO{Simon: or may be better, present BIP architectures and the use-case \_BEFORE\_ The pNets definition, and define the encoding here}
-
-\section{Running example}
-\label{section:FailureTimerMax}
-\TODO{1.5 page including figures ?}
+As a running example we use the Failure Monitor architecture from the
+CubETH nanosatellite on-board software
+case-study~\cite{CubETH-case-study} realised using BIP.  BIP
+(Behaviour-Interaction-Priority)~\cite{bip} is a framework for the
+component-based design of concurrent software and systems.  In
+particular, the BIP tool-set comprises compilers for generating C/C++
+code, executable by linking with one of the dedicated engines, which
+implement the BIP operational semantics.  This approach ensures that
+any property, shown to hold on a given BIP model, will also hold by
+construction on the generated code.
+
+In this context, the notion of \emph{architecture} was proposed
+in~\cite{AttieBBJS16-architectures-faoc} as a mechanism for ensuring
+correctness by construction during the design of BIP models.
+Architecutres can be viewed as operators transforming BIP models.
+They formalise design patterns, which enforce global properties
+characterising the coordination among the components of the system.
+The architecture-based design process in BIP takes as input a set of
+components providing basic functionality of the system and a set of
+temporal properties that must be enforced in the final system.  For
+each property, a corresponding architecture is identified\,\footnote{%
+%
+  The current approach relies on taxonomies of predefined
+  architectures.  Future work may include automatic synthesis of
+  architectures from, \eg CTL or a similar logic. 
+%
+} and applied to the model, thereby potentially introducing additional
+coordinator components and modifying the connectors that define
+synchronisation patterns among ports of components.
+In~\cite{AttieBBJS16-architectures-faoc}, it was shown that
+application of architectures is compositional \wrt safety properties,
+\ie when several architectures are applied, each enforcing a safety
+property, the resulting system satisfies their conjunction.
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=0.9\columnwidth]{XFIG/BIPspec-ArchFailureTimerMax-v2}
+  \caption{The BIP specification of the Failure Monitor architecture}
+  \label{schema:ArchFailure:BIP}
+\end{figure}
+
+Figure~\ref{schema:ArchFailure:BIP} shows a refined version of the
+Failure Monitor architecture used in~\cite{CubETH-case-study}.
+Contrary to standard BIP models, architectures comprise one or several
+\emph{operand} components, whereof only the set of \emph{ports} is
+given.  Here, the operand component is $B$ and its interface consists
+of the ports $\PortFinish$, $\PortResume$ and $\PortFail$.  The two
+\emph{coordinator} components\mdash $\NameCtrl$ and $\NameTimer$\mdash
+are standard BIP components insofar as they also have their
+\emph{behaviour} specified by finite automata extended with local data
+variables.  Transitions of these automata are labelled with the ports
+of the corresponding component, Boolean guards and update functions on
+local variables.  For instance the loop transition $\tstate{1}
+\goesto{\PortTick, \GuardTick[], \TimerUpd[]} \tstate{1}$ in the
+$\NameTimer$ component is labeled by the port $\PortTick$, it can be
+fired only when the current value of the local variable $t$ is greater
+than $0$.  Upon firing, this transition decrements the value of $t$ by
+$1$.  When omitted, the default guard (resp. update function) is the
+constant predicate $\true$ (resp. the $\mathit{skip}$ operator).  The
+constant $\mathrm{Max}$, in $\tstate{0} \goesto{\PortStart,
+  \TimerInit[]} \tstate{1}$, is a parameter of the architecture.
 
@@
 
+\TODO{1.5 page including figures ?}
+
+\TODO{Simon: can you do this in less than one page ? If you prefer,
+  merge with ``Running example'' may be easier to describe the syntax}
+
+\TODO{Simon: or may be better, present BIP architectures and the use-case \_BEFORE\_ The pNets definition, and define the encoding here}
+
 \TODO{Should have here both the original BIP drawing (Simon), and the
@@
    \centering
-   \includegraphics[width=\columnwidth]{XFIG/BIPspec-ArchFailureTimerMax-v2}
-   \caption{The BIP specification of the FailureTimer architecture}
-   \label{schema:ArchFailure:BIP}
- \end{figure}
-%
-   %% \hfill
-%
- \begin{figure}[t]
-   \centering
-   \includegraphics[width=\columnwidth]{XFIG/FailureTimerPNET}
+   \includegraphics[width=0.9\columnwidth]{XFIG/FailureTimerPNET}
    \caption{pNet encoding of the FailureTimer architecture}
@@
 
+\subsection{Simplification of Predicates}
+\ERIC{: motivated, add refs, and an abstract presentation of stuff
+  from pages 19-20. The following is NOT a good example, we should
+  rather use a pNet with at least 2 levels, to have real intermediate
+variables; here b0, b1, b2 are NOT intermediate variables... and the
+predicate simplification is using `some form of ``tautology checking''
+rather thanm rewritting.}
+
+Before:
+  	\begin{mathpar}
+	\inferrule*[myfraction=\reddottedrule]
+	{\{s0~{\xrightarrow{fail(true)}} ~s1, t0~{\xrightarrow{start(true)}} ~t1\}
+	  \{\xrightarrow{hb}\},\\
+\qquad b1=true \land b2=true \land hb=fail(b0) \land b1=b2 \land (b1\cup b2
+\implies b0) \land v=\underline{fail}, \{t := 4\}
+        }
+	{<s0,t0> \xrightarrow {v} <s1,t1>}
+	\end{mathpar}
+
+After:
+          	\begin{mathpar}
+	\inferrule*[myfraction=\reddottedrule]
+	{\{s0~{\xrightarrow{fail(true)}} ~s1, t0~{\xrightarrow{start(true)}} ~t1\}
+	  \{\xrightarrow{hb}\}, hb=fail(true) \land v=\underline{fail}, \{t := 4\}
+        }
+	{<s0,t0> \xrightarrow {v} <s1,t1>}
+	\end{mathpar}
+
 \subsection{Result of the running example}
@@
 \appendix
-%\section{Appendix}
+\section{Appendix}
 The following appendices are included for the convenience of reviewers.
@@
 extended version containing all technical detials, proofs, and more examples.
-
-These are organized in th efollowing way:
-
-\begin{enumerate}
-\item[A] pNet semantic rules
-\item[B] Variable managment
-\item[C] Translation to SMTlib input language
-\item[D] Well-formness and typing of expressions
-\item[E]
-
-\end{enumerate}
 
@@
 
-% \section{More details on the generation algorithm}
-
-\section{Variable managment}
-The variables in each synchronisation vector are considered local: for
-a given pNet expression, we must have fresh local variables for each
-occurrence of a vector (= each time we instantiate rule
-Tr2). Similarly the state variables of each copy of a given pLTS in
-the system, must be distinct, and those created for each application
-of Tr2 have to be fresh and all distinct. This will be implemented
-within the open-automaton generation algorithm, e.g. using name
-generation using a global counter as a suffix.
-\TODO{add structure of generated names}
-
-\section{Translation to SMTlib input language}
+\section{More details on the generation algorithm}
+
+\subsection{Variable managment}
+The variables in each synchronisation vector are considered local: for a given pNet expression, we must have fresh local variables for each occurrence of a vector (= each time we instantiate rule Tr2).
+Similarly the state variables of each copy of a given pLTS in the system, must be distinct, and those created for each application of Tr2 have to be fresh and all distinct.
+This will be implemented within the open-automaton generation algorithm, e.g.
+using name generation using a global counter as a suffix.
+
+\subsection{Translation to SMTlib input language}
 In order to submit satisfiability problems to Z3 (for the predicates
@@
 
-\subsection{Definition of an algebra presentation}
 We have a minimal, predefined algebra presentation for all pNets, including
@@
                 \\\specialrule{0em}{1pt}{1pt} 
-		Action 			&  $\texttt{FUN}$ &
+		Action 			&  $texttt{FUN}$ &
                 \\\specialrule{0em}{1pt}{1pt}
@@
                 \textsl{for any sort} & & $=,\ \ne$
-		\\\hline
-	\end{tabular}
-\end{table}
-
-\begin{table}\caption{\label{table:BIPalgebra}\leftline{Additional
-      operator for the BIP algebra}}
-	\begin{tabular}{p{3cm}p{3cm}p{6cm}}
-		\hline\specialrule{0em}{1pt}{1pt}
-		Sort & Constructors & Other Operators
-                \\\hline\specialrule{0em}{1pt}{1pt} 
-		Action 			&  $\texttt{FUN\_Action\_Bool}$ &
 		\\\hline
@@
 
-\begin{table}\caption{\label{table:BIPalgebra}\leftline{Additional
-      sorts and operators for the CCS algebra}}
-	\begin{tabular}{p{3cm}p{3cm}p{6cm}}
-		\hline\specialrule{0em}{1pt}{1pt}
-		Sort & Constructors & Other Operators
-                \\\specialrule{0em}{1pt}{1pt}
-		\hline\specialrule{0em}{3pt}{3pt}
-		Channel, Data    			&
-                $\emptyset$&
-                $\emptyset$
-                \\\specialrule{0em}{1pt}{1pt} 
-		Action 			&  $\texttt{Emit(c,v)},\texttt{Receive(c,v)},\texttt{Tau}$ &
-		\\\hline
-	\end{tabular}
-\end{table}
-
-Then in pNet API these operators or constants can be declared as:
-\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
+Then in pNet API these operators or constants (seemed as non-parameter operators) can be declared as:
+\begin{lstlisting}[basicstyle=\footnotesize\ttfamily, language=java, frame=single]
 AlgebraSort Action = new AlgebraSortImpl("Action");
@@
 
-%\subsection{Constants and variables in pNets and in open transitions}
-\subsection{Extended presentation, and Environment}
+\paragraph{Expressions}
+Once an algebra presentation is defined, we can construct expressions
+of the term algebra, using variables and operators:
+
+\begin{definition}
+  Let $\mathcal{V}$ be a set of variables. The Term Algebra
+  $\Sigma_{\mathcal{P},\mathcal{V}}$ is the set of:
+  \begin{itemize}
+  \item variables $x \in \mathcal{V}$
+  \item terms (or expressions) $op (arg_1, ... , arg_n)$ with $op$ an operator in
+  $\mathcal{P}$ of arity $n$, and each $arg_i$ an expression.
+  \end{itemize} 
+\end{definition}
+
+\paragraph{Constants and variables in pNets and in open transitions}
 
@@
 
-\section{Well-formness and typing of expressions}
+\paragraph{Well-formed and well-typed expressions}
 
@@
 expressions respect the arity of operators), and typing rules.
-%\TODO{Eric: refer in the appendix header}
+\TODO{Eric: refer in the appendix header}
 
@@
 
-\section{Map to SMT-LIB language}
+\subsubsection{Map to SMT-LIB language}
 The pNet elements, as defined above, can be full translated into
@@
 In this section we shall define separately the translation of the
-extended algebra presentation for one pNet (so it will be common for
-the study of all OTs of one use-case); and the translation of each
-predicate (of an open-transition) of this pNet.
+(extended) algebra presentation for one pNet (so it will be fixed for
+the study of one use-case); and the translation of each predicate in
+the context of an open-transition of this pNet.
 
@@
 \subsection{Simplification of Predicates}
-\subsection{Simplification of Predicates}
-\ERIC{: motivated, add refs, and an abstract presentation of stuff
-  from pages 19-20. The following is NOT a good example, we should
-  rather use a pNet with at least 2 levels, to have real intermediate
-variables; here b0, b1, b2 are NOT intermediate variables... and the
-predicate simplification is using `some form of ``tautology checking''
-rather thanm rewritting.}
-
-Before:
-  	\begin{mathpar}
-	\inferrule*[myfraction=\reddottedrule]
-	{\{s0~{\xrightarrow{fail(true)}} ~s1, t0~{\xrightarrow{start(true)}} ~t1\}
-	  \{\xrightarrow{hb}\},\\
-\qquad b1=true \land b2=true \land hb=fail(b0) \land b1=b2 \land (b1\cup b2
-\implies b0) \land v=\underline{fail}, \{t := 4\}
-        }
-	{<s0,t0> \xrightarrow {v} <s1,t1>}
-	\end{mathpar}
-
-After:
-          	\begin{mathpar}
-	\inferrule*[myfraction=\reddottedrule]
-	{\{s0~{\xrightarrow{fail(true)}} ~s1, t0~{\xrightarrow{start(true)}} ~t1\}
-	  \{\xrightarrow{hb}\}, hb=fail(true) \land v=\underline{fail}, \{t := 4\}
-        }
-	{<s0,t0> \xrightarrow {v} <s1,t1>}
-	\end{mathpar}
+\TODO{[Eric]: Motivate, and refs  -- reduce the section here to approx
+  half a page (from the next two pages...)}
 

### 2018-01-17 2017-Xudong-SMT/FM-2018-extended.tex
Simon's ideal (too long?) presentation of BIP, architectures and Failure Monitor.

@@
     margin=0pt,
-    width=0.8\textwidth,
+    %% width=0.8\textwidth,
+    aboveskip=4pt,
+    belowskip=-12pt,
 ]{caption}
 \usepackage[list=true]{subcaption}
+
+\usepackage{soul}
+\usepackage[colorinlistoftodos,bordercolor=white]{todonotes}
+%% \usepackage[disable,colorinlistoftodos,bordercolor=white]{todonotes}
+
+\newcommand{\noteSB}[2][color=green!40, size=\tiny]{\todo[#1]{{\bf Note: } {#2}}}
+\newcommand{\noteInSB}[2][inline,color=green!40]{\todo[#1]{{\bf Note: } {#2}}}
 
@@
 code, executable by linking with one of the dedicated engines, which
-implement the BIP operational semantics.  This approach ensures that
-any property, shown to hold on a given BIP model, will also hold by
-construction on the generated code.
+implement the BIP operational semantics~\cite{BliSif08-acp-tc}.  This
+approach ensures that any property, shown to hold on a given BIP
+model, will also hold by construction on the generated code.
 
@@
   \centering
-  \includegraphics[width=0.9\columnwidth]{XFIG/BIPspec-ArchFailureTimerMax-v2}
+  \includegraphics[width=0.8\columnwidth]{XFIG/BIPspec-ArchFailureTimerMax-v2}
   \caption{The BIP specification of the Failure Monitor architecture}
@@
 \emph{operand} components, whereof only the set of \emph{ports} is
-given.  Here, the operand component is $B$ and its interface consists
-of the ports $\PortFinish$, $\PortResume$ and $\PortFail$.  The two
-\emph{coordinator} components\mdash $\NameCtrl$ and $\NameTimer$\mdash
-are standard BIP components insofar as they also have their
-\emph{behaviour} specified by finite automata extended with local data
-variables.  Transitions of these automata are labelled with the ports
-of the corresponding component, Boolean guards and update functions on
-local variables.  For instance the loop transition $\tstate{1}
-\goesto{\PortTick, \GuardTick[], \TimerUpd[]} \tstate{1}$ in the
-$\NameTimer$ component is labeled by the port $\PortTick$, it can be
-fired only when the current value of the local variable $t$ is greater
-than $0$.  Upon firing, this transition decrements the value of $t$ by
-$1$.  When omitted, the default guard (resp. update function) is the
-constant predicate $\true$ (resp. the $\mathit{skip}$ operator).  The
-constant $\mathrm{Max}$, in $\tstate{0} \goesto{\PortStart,
-  \TimerInit[]} \tstate{1}$, is a parameter of the architecture.
+given.  Here, the operand component is $\NameOprnd$ and its interface
+consists of the ports $\PortFinish$, $\PortResume$ and $\PortFail$.
+The two \emph{coordinator} components\mdash $\NameCtrl$ and
+$\NameTimer$\mdash are standard BIP components insofar as they also
+have their \emph{behaviour} specified by finite automata extended with
+local data variables.  Transitions of these automata are labelled with
+the ports of the corresponding component, Boolean guards and update
+functions on local variables.  For instance the loop transition
+$\tstate{1} \goesto{\PortTick, \GuardTick[], \TimerUpd[]} \tstate{1}$
+in the $\NameTimer$ component is labeled by the port $\PortTick$, it
+can be fired only when the current value of the local variable $t$ is
+greater than $0$.  Upon firing, this transition decrements the value
+of $t$ by $1$.  When omitted, the default guard (resp. update
+function) is the constant predicate $\true$ (resp. the $\mathit{skip}$
+operator).  The constant $\mathrm{Max}$, in $\tstate{0}
+\goesto{\PortStart, \TimerInit[]} \tstate{1}$, is a parameter of the
+architecture.
+
+Connectors are hierarchical, tree-like structures with component ports
+at the leaves.  They define sets of \emph{interactions}, based on the
+attributes of the connected ports~\cite{BliSif08-acp-tc}, which may be
+either \emph{trigger} (triangles in Fig.~\ref{schema:ArchFailure:BIP})
+or \emph{synchron} (bullets in Fig.~\ref{schema:ArchFailure:BIP}).
+%
+If all sub-connectors of a connector are synchrons, then an
+interaction may be executed by the connector only if each subconnector
+can contribute.
+%
+If at least one of the sub-connectors is a trigger, then any
+interaction consisting of contributions of any set of sub-connectors,
+\emph{involving at least one of the triggers}, can be executed.
+%
+For instance, the two ports $\NameTimer.\PortStart$ and
+$\NameCtrl.\PortFail$ are always synchronised, since they belong to
+the same binary sub-connector, where they are both synchrons.  In
+particular, this means that whenever the transition $\cstate{0}
+\goesto{\PortFail} \cstate{1}$ is fired, so is the transition
+$\tstate{0} \goesto{\PortStart, \TimerInit[]} \tstate{1}$,
+initialising the timer.  The binary connector $\NameTimer.\PortStart
+\bullet\!\!\!-\!\!\!-\!\!\!\bullet \NameCtrl.\PortFail$ is a
+sub-connector of a hierarchical connector, where the port
+$\NameOprnd.\PortFail$ is a trigger.  Thus, the above interaction can
+only happen together with $\NameOprnd.\PortFail$, thus forming a
+ternary interaction.  On the contrary, being a trigger, the port
+$\NameOprnd.\PortFail$ can fire alone, forming a singleton
+interaction.  The composition semantics of BIP systems consists in
+firing exactly one interaction, enabled through at least one of the
+connectors, at each execution round.
+
+Finally, \emph{priorities}\mdash defined by a strict partial order on
+the set of possible interactions\mdash narrow the choice among the
+enabled interactions at any given round.  The default priority is the
+so-called \emph{maximal progress}, whereby among any two interactions
+$a \subset b$ (as sets of ports), $b$ has higher priority than $a$.
+For example, the port $\NameOprnd.\PortFail$ will never fire alone in
+a global state, where both $\NameTimer.\PortStart$ and
+$\NameCtrl.\PortFail$ are enabled.
+
+Application of the Failure Monitor architecture ensures that, whenever
+a failure is registered in the operand component, the system will be
+reset, unless a resumption is registered within $\mathrm{Max}$ time
+units.\noteSB{Here, it would be nice to explain the role of the
+  singleton connectors, but that would take too much space.}
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=0.8\columnwidth]{XFIG/FailureTimerPNET}
+  \caption{pNet encoding of the FailureTimer architecture}
+  \label{schema:ArchFailure:pNet}
+\end{figure}
 
@@
 
-\TODO{1.5 page including figures ?}
-
-\TODO{Simon: can you do this in less than one page ? If you prefer,
-  merge with ``Running example'' may be easier to describe the syntax}
-
-\TODO{Simon: or may be better, present BIP architectures and the use-case \_BEFORE\_ The pNets definition, and define the encoding here}
-
-\TODO{Should have here both the original BIP drawing (Simon), and the
-  pNet encoding (fig by Eric)}
-
- \begin{figure}[t]
-   \centering
-   \includegraphics[width=0.9\columnwidth]{XFIG/FailureTimerPNET}
-   \caption{pNet encoding of the FailureTimer architecture}
-   \label{schema:ArchFailure:pNet}
- \end{figure}
+%% \TODO{1.5 page including figures ?}
+
+%% \TODO{Simon: can you do this in less than one page ? If you prefer,
+%%   merge with ``Running example'' may be easier to describe the syntax}
+
+%% \TODO{Simon: or may be better, present BIP architectures and the use-case \_BEFORE\_ The pNets definition, and define the encoding here}
+
+%% \TODO{Should have here both the original BIP drawing (Simon), and the
+%%   pNet encoding (fig by Eric)}
 

### 2018-01-17 2017-Xudong-SMT/FM-2018-extended.tex
Finished the Running example section. 2.5 pages all-included, with both figures

@@
 
-\usepackage{soul}
+\usepackage{soul}               % Highlighting: \hl, \so, \ul
+\soulregister{\st}{8}
+\soulregister\cite7
+\soulregister\citep7
+\soulregister\secn7
+\soulregister\ref7
+\soulregister\pageref7
+\soulregister{\em}{0}
+\soulregister{\bf}{0}
+\soulregister{\fig}{7}
+\soulregister{\ie}{0}
+\soulregister{\etc}{0}
+\soulregister{\eg}{0}
+\soulregister{\wrt}{0}
+\soulregister{\resp}{0}
+\soulregister{\cf}{0}
+\soulregister{\mdash}{0}
+\soulregister{\ndash}{0}
+
 \usepackage[colorinlistoftodos,bordercolor=white]{todonotes}
@@
 \newcommand{\wrt}[1][\ ]{w.r.t.#1}
+\newcommand{\resp}[1][\ ]{resp.#1}
 
@@
 \newcommand{\true}{\ensuremath{\mathit{true}}}
+\newcommand{\false}{\ensuremath{\mathit{false}}}
 
@@
 local data variables.  Transitions of these automata are labelled with
-the ports of the corresponding component, Boolean guards and update
+the ports of the corresponding components, Boolean guards and update
 functions on local variables.  For instance the loop transition
@@
 greater than $0$.  Upon firing, this transition decrements the value
-of $t$ by $1$.  When omitted, the default guard (resp. update
-function) is the constant predicate $\true$ (resp. the $\mathit{skip}$
+of $t$ by $1$.  When omitted, the default guard (\resp update
+function) is the constant predicate $\true$ (\resp the $\mathit{skip}$
 operator).  The constant $\mathrm{Max}$, in $\tstate{0}
@@
 $\NameOprnd.\PortFail$ is a trigger.  Thus, the above interaction can
-only happen together with $\NameOprnd.\PortFail$, thus forming a
+only happen together with $\NameOprnd.\PortFail$, forming a
 ternary interaction.  On the contrary, being a trigger, the port
@@
 firing exactly one interaction, enabled through at least one of the
-connectors, at each execution round.
+top-level connectors, at each execution round.
 
@@
 the set of possible interactions\mdash narrow the choice among the
-enabled interactions at any given round.  The default priority is the
+enabled interactions at any given execution round.  The default priority is the
 so-called \emph{maximal progress}, whereby among any two interactions
@@
 \end{figure}
+
+\noteSB{SV2 should not be closed;\\SV0, SV1: $\cup \rightarrow \lor$}\hl{%
+%
+Figure~\ref{schema:ArchFailure:pNet} shows a pNet encoding of the
+above Failure Monitor architecture.  This encoding is structural: each
+coordinator component is encoded as a pLTS, the operand
+component\mdash as a hole; connectors of the BIP model are encoded as
+synchronisation vectors.  Each connector that does not involve
+triggers is trivially encoded by a synchronisation vector comprising
+the same ports.  In order to encode the semantics of the connectors
+involving triggers, we 1)~in the pLTS encoding the coordinator
+components, add loop transitions to ensure that all ports involved in
+such connectors are enabled in all states, 2)~associate a Boolean
+value to each of these ports: the original transitions carry the value
+$\true$ (\eg $\cstate{0} \goesto{\PortFail(\true)} \cstate{1}$), the
+added loops carry the value $\false$ (\eg $\cstate{2}
+\goesto{\PortFail(\false)} \cstate{2}$), 3)~add to the corresponding
+synchronisation vectors the Boolean predicate encoding the connector
+structure.  For example, $SV0$ encodes the connector discussed above:
+the predicate $b1 = b2 \land b1 \lor b2 \Rightarrow b0$ means that the
+``true'' transitions $\NameCtrl.\PortFail$ and $\NameTimer.\PortStart$
+can only fire together ($b1 = b2$) and whenever one of them fires,
+$\NameOprnd.\PortFail$ must fire also ($b1 \lor b2 \Rightarrow b0$).
+This encoding can be systematically obtained for any hierarchical BIP
+connector~\cite{BliSif10-causal-fmsd}.
+%
+}
+\noteSB{
+%
+  Eric, could you please check my pNet terminology in this paragraph?
+%
+}
+%
+Although, for the sake of brevity, this encoding does not translate
+the maximal progress priority, it can be easily extended to do so, by
+introducing an additional Boolean variable for each relevant port.
 

### 2018-01-18 2017-Xudong-SMT/FM-2018-extended.tex
proofreading of BIP part

@@
 \documentclass{lncs/llncs}
+\usepackage{etex}
 
@@
 \usepackage{soul}               % Highlighting: \hl, \so, \ul
+
 \soulregister{\st}{8}
@@
 
-\newcommand{\noteSB}[2][color=green!40, size=\tiny]{\todo[#1]{{\bf Note: } {#2}}}
+\newcommand{\noteSB}[2][color=green!40, size=\tiny]{\todo[#1]{{\bf
+      Note: } {#2}}}
+\newcommand{\noteEM}[2][color=blue!40, size=\tiny]{\todo[#1]{{\bf Eric: } {#2}}}
 \newcommand{\noteInSB}[2][inline,color=green!40]{\todo[#1]{{\bf Note: } {#2}}}
@@
 \ref{section:pnets} we give a description and a formal definition of
-the pNet model, as found in previous publications. Then in
-\ref{section:examples} we present a simple example that will
-illustrate the rest of the paper.
-Section \ref{section:op-semantics} recalls the operational semantics
-of pNet, including its structural rules.
-Section \ref{section:implementation} explains in details our
-implementation within the Vercors platform, and shows the full result of
-the semantic computation on the running example.
-Finally we conclude and discuss perspectives in section
+the pNet model, as found in previous publications. Then in section
+\ref{section:examples} we present our use-case, based on an
+industrial-inspired study of the control software of nano-satellites,
+specified using the BIP language. 
+Section \ref{section:op-semantics} recalls briefly the operational semantics
+of pNet.
+Section \ref{section:implementation} explains in details the algorithm
+used to compute this semantics, including the interaction with Z3, and
+shows the full result of the semantic computation on the running example.
+Finally we conclude and discuss perspectives.
 \ref{section:conclusion}.
@@
 
+In Fig.~\ref{schema:ArchFailure:pNet} we show examples of these
+constructs, with 2 pLTSs and one pNet node encoding our use-case.
+
 \section{Running example}
@@
 correctness by construction during the design of BIP models.
-Architecutres can be viewed as operators transforming BIP models.
+Architectures can be viewed as operators transforming BIP models.
 They formalise design patterns, which enforce global properties
@@
   \centering
-  \includegraphics[width=0.8\columnwidth]{XFIG/FailureTimerPNET}
-  \caption{pNet encoding of the FailureTimer architecture}
+  \includegraphics[width=0.9\columnwidth]{XFIG/FailureTimerPNET}
+  \caption{pNet encoding of the FailureTimer architecture
+  \noteEM{A little too small for me, my eyes are getting tired...}}
   \label{schema:ArchFailure:pNet}
@@
 
-\noteSB{SV2 should not be closed;\\SV0, SV1: $\cup \rightarrow \lor$}\hl{%
+\noteSB{SV2 should not be closed;\\SV0, SV1: $\cup \rightarrow \lor$}
+%\hl{%
 %
@@
 structure.  For example, $SV0$ encodes the connector discussed above:
-the predicate $b1 = b2 \land b1 \lor b2 \Rightarrow b0$ means that the
+the predicate $(b1=b2) \land (b1\lor b2 \Rightarrow b0)$ means that the
 ``true'' transitions $\NameCtrl.\PortFail$ and $\NameTimer.\PortStart$
@@
 %
-}
+%}
 \noteSB{
@@
 }
+\noteEM{Done, it's ok.}
 %
@@
   \texttt{fail}. The local variable \texttt{t} of the \texttt{Timer}
-  is assigned to its initial value \texttt{Max}. \TODO{may be the
-    place to mention the ``fresh variable'' names, rather than in th
-    eZ3 syntax figure}
+  is assigned to its initial value \texttt{Max}.
+In fact this OT is displayed in a simplied, human readable form. The
+raw output of the tool is slightly more difficult to read, in
+particular it uses structured names for the fresh variables generated
+by the algorithm, allowing tracability of the result (see
+Appendix~\ref{appendix:varaibles}). A full output of 
+the use-case is provided in Appendice~\ref{appendix:fullOutput}.
+
   \label{OT:lotos-composed}
@@
 \section{Variable managment}
+\label{appendix:varaibles}
 The variables in each synchronisation vector are considered local: for
@@
 
-\section{Full examples}
-
-\subsection{Full input for the FailureTimer architecture}
-\subsection{Full output for the FailureTimer open automaton}
+\section{Full output for the FailureTimer open automaton}
+\label{appendix:fullOutput}
 

### 2018-01-18 2017-Xudong-SMT/FM-2018-extended.tex
Change the Z3 input example.
Choose another UNSAT ot.
Improve the transition rules to be consist with the former defined functions.

@@
   \caption{pNet encoding of the FailureTimer architecture
-  \noteEM{A little too small for me, my eyes are getting tired...}}
+  \noteEM[inline]{A little too small for me, my eyes are getting tired...}}
   \label{schema:ArchFailure:pNet}
@@
 cartesian product of sets :  
-\[\texttt{COMB} : (\inactive\cup ot_1) \times (\inactive\cup ot_2)\times ... \times (\inactive\cup ot_n) .\]
+$\texttt{COMB} : (\inactive\cup ot_1) \times (\inactive\cup ot_2)\times ... \times (\inactive\cup ot_n) .$
 
@@
 $\begin{array}{r@{}l}
-    ot  = &\openrule{\{0 \xrightarrow{\OTvar{resume(false)}} 0, 0 \xrightarrow{\OTvar{start(true)}} 1\}, ~~\{\xrightarrow{hb}\},~~\OTvar{resume(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
-    			     \OTland \OTvar{start(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)} \OTland \OTvar{hb}=\OTvar{fail(}\OTvar{b}_0\OTvar{)} \OTland \OTvar{v}=\OTvar{\underline{fail}}\\
-			     \OTland \OTvar{b}_1 = \OTvar{b}_2 \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
-    	   {\ostate{00} \xrightarrow{\OTvar{v}} \ostate{01}}\\
+    ot  = &\openrule{\{s1 \xrightarrow{\OTvar{fail(false)}} s1, t1 \xrightarrow{\OTvar{resume(true)}} t0\}, ~~\{\xrightarrow{hb}\},~~\OTvar{fail(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
+    \OTland \OTvar{resume(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland \OTvar{hb}=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\OTland \OTvar{v}=\OTvar{\underline{fail}}\OTland \OTvar{b}_1 = \OTvar{b}_2\\
+    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
+    	   {\ostate{s1,t1} \xrightarrow{\OTvar{v}} \ostate{s1,t0}}\\
   \end{array}$
@@
 AlgebraSort Data = new AlgebraSortImpl("Data");
-Action.addConstructor("Emit", 
-	{"Chan_E", "Value_E"}, {Channel, Data});
-Action.addConstructor("Receive", 
-	{"Chan_E", "Value_E"}, {Channel, Data});
+Action.addConstructor("Emit", {"Chan_E", "Value_E"}, {Channel, Data});
+Action.addConstructor("Receive", {"Chan_E", "Value_E"}, {Channel, Data});
 Action.addConstructor("Tau");
@@
   (declare-datatypes ()
-      ((Action (Emit (Chan\_E Channel) (Value\_E Data))
-               (Receive (Chan\_R Channel) (Value\_R Data))
+      ((Action (Emit (Chan_E Channel) (Value_E Data))
+               (Receive (Chan_R Channel) (Value_R Data))
                Tau )))
@@
 		\\
-		$\dfrac{Pred \translate lst_1~~Ass \translate lst_2}{ot(Pred, Assign) \translate lst_1 lst_2}$
+		$\dfrac{Pred \translate lst_1~~Ass \translate lst_2}{ot(Pred, Ass) \translate lst_1 lst_2}$
 		\\\specialrule{0em}{3pt}{3pt}
@@
 		\\
-		$\dfrac{Assign = \bigwedge\limits_{k\in K}(x_k, a_k)~~x_k\in SVar(gs)~~a_k = Ass(x_k)}{Assign \translate \texttt{map} \translate (x_k, a_k)}$
+		$\dfrac{Ass = \bigwedge\limits_{k\in K}(x_k, a_k)~~x_k\in SVar(gs)~~a_k = Assigns(x_k)}{Ass \translate \texttt{map} \translate (x_k, a_k)}$
 		\\\specialrule{0em}{3pt}{3pt}		
@@
 
+\begin{figure}[h]  
+$\begin{array}{r@{}l}
+    ot_1  = &\openrule{\{s0 \xrightarrow{\OTvar{fail(true)}} s1, t0 \xrightarrow{\OTvar{start(true)}} t1\}, ~~\{\xrightarrow{hb_1}\},~~\OTvar{fail(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
+    \OTland \OTvar{start(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland hb_1=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\OTland v_1=\OTvar{\underline{fail}}\OTland \OTvar{b}_1 = \OTvar{b}_2
+    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
+    	   {\ostate{s0,t0} \xrightarrow{v_1} \ostate{s1,t1}}\\
+\end{array}$
+
+$\begin{array}{r@{}l}
+    ot_2  = &\openrule{\{s0 \xrightarrow{\OTvar{resume(false)}} s0, t0 \xrightarrow{\OTvar{resume(false)}} t0\}, ~~\{\xrightarrow{hb_2}\},~~\OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_1\OTvar{)}\\
+    \OTland \OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_2=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\OTland v_2=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
+    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{t := 4\}}
+    	    {\ostate{s0,t0} \xrightarrow{v_2} \ostate{s0,t0}}\\
+\end{array}$
+
+$\begin{array}{r@{}l}
+    ot_3  = &\openrule{\{\}, ~~\{\xrightarrow{hb_3}\},~~hb_3=\OTvar{finish}\OTland v_3=\OTvar{finish}, ~~\{\}}
+    	    {\ostate{s0,t0} \xrightarrow{v_3} \ostate{s0,t0}}\\
+\end{array}$
+
+$\begin{array}{r@{}l}
+    ot_4  = &\openrule{\{s1 \xrightarrow{\OTvar{fail(false)}} s1, t1 \xrightarrow{\OTvar{start(false)}} t1\}, ~~\{\xrightarrow{hb_4}\},~~\OTvar{fail(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
+    \OTland \OTvar{start(false)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland hb_4=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\OTland v_4=\OTvar{\underline{fail}}\OTland \OTvar{b}_1 = \OTvar{b}_2
+    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
+    	   {\ostate{s1,t1} \xrightarrow{v_4} \ostate{s1,t1}}\\
+\end{array}$
+
+$\begin{array}{r@{}l}
+    ot_5  = &\openrule{\{s1 \xrightarrow{\OTvar{resume(true)}} s0, t1 \xrightarrow{\OTvar{resume(true)}} t0\}, ~~\{\xrightarrow{hb_5}\},~~\OTvar{resume(true)}=\OTvar{resume(}\OTvar{b}_1\OTvar{)}\\
+    \OTland \OTvar{resume(true)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_2=\OTvar{resume(}\OTvar{b}_0\OTvar{)}\OTland v_5=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
+    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
+    	    {\ostate{s1,t1} \xrightarrow{v_5} \ostate{s0,t0}}\\
+\end{array}$
+
+$\begin{array}{r@{}l}
+    ot_6  = &\openrule{\{t1 \xrightarrow{\OTvar{tick}} t1\}, ~~\{\},~~t\neq 0\OTland v_6=\OTvar{\underline{tick}}, ~~\{t := t-1 \}}
+    	   {\ostate{s1,t1} \xrightarrow{v_6} \ostate{s1,t0}}\\
+\end{array}$
+
+$\begin{array}{r@{}l}
+    ot_7  = &\openrule{\{\}, ~~\{\xrightarrow{hb_7}\},~~hb_7=\OTvar{finish}\OTland v_7=\OTvar{finish}, ~~\{\}}
+    	    {\ostate{s1,t1} \xrightarrow{v_7} \ostate{s1,t1}}\\
+\end{array}$
+
+$\begin{array}{r@{}l}
+    ot_8  = &\openrule{\{s1 \xrightarrow{\OTvar{timeout}} s2, t1 \xrightarrow{\OTvar{timeout}} t0\}, ~~\{\},~~t=0\OTland v_8=ask, ~~\{\}}
+    	   {\ostate{s1,t1} \xrightarrow{v_8} \ostate{s2,t0}}\\
+\end{array}$
+
+$\begin{array}{r@{}l}
+    ot_9  = &\openrule{\{s2 \xrightarrow{\OTvar{resume(false)}} s2, t0 \xrightarrow{\OTvar{resume(false)}} t0\}, ~~\{\xrightarrow{hb_9}\},~~\OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_1\OTvar{)}\\
+    \OTland \OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_9=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\OTland v_9=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
+    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
+    	    {\ostate{s2,t0} \xrightarrow{v_9} \ostate{s2,t0}}\\
+\end{array}$
+
+$\begin{array}{r@{}l}
+    ot_{10}  = &\openrule{\{s2 \xrightarrow{\OTvar{reset}} s0\}, ~~\{\},~~v_{10}=\OTvar{reset}, ~~\{\}}
+    	   {\ostate{s2,t0} \xrightarrow{v_{10}} \ostate{s0,t0}}\\
+\end{array}$
+
+$\begin{array}{r@{}l}
+    ot_{11}  = &\openrule{\{\}, ~~\{hb_{11}\},~~hb_{11}=\OTvar{finish}\OTland v_{11}=\OTvar{finish}, ~~\{\}}
+    	   {\ostate{s2,t0} \xrightarrow{v_{11}} \ostate{s2,t0}}\\
+\end{array}$
+\caption{The open transitions of the open automaton}  \label{schema:ots}
+\end{figure}
+
 \subsection{Scaling up: several subsystems on the same bus}

### 2018-01-18 2017-Xudong-SMT/FM-2018-extended.tex
typos
assignments, and solved many references problems

@@
 units.\noteSB{Here, it would be nice to explain the role of the
-  singleton connectors, but that would take too much space.}
+  singleton connectors, but that would take too much space. AGREED}
 
@@
   \caption{pNet encoding of the FailureTimer architecture
-  \noteEM[inline]{A little too small for me, my eyes are getting tired...}}
+  \noteEM[inline]{Was a little too small for me, my eyes are getting tired...}}
   \label{schema:ArchFailure:pNet}
@@
 
-\noteSB{SV2 should not be closed;\\SV0, SV1: $\cup \rightarrow \lor$}
+\noteSB{SV2 should not be closed;\\SV0, SV1: $\cup \rightarrow \lor$... DONE}
 %\hl{%
@@
 by the algorithm, allowing tracability of the result (see
-Appendix~\ref{appendix:varaibles}). A full output of 
-the use-case is provided in Appendice~\ref{appendix:fullOutput}.
-
-  \label{OT:lotos-composed}
+appendix~\ref{appendix:variables}). A full output of 
+the use-case is provided in appendice~\ref{appendix:fullOutput}.
+
+  \label{OT:example-1}
         \begin{mathpar}
@@
 \cite{henrio:Forte2016}. For convenience we include these 
-rules in Appendix \ref{appendix:semRules}.
+rules in appendix \ref{appendix:semRules}.
 
@@
 \label{section:pruning}
-%We have used a brute-force method to generate all the possible open
-%transitions in the open automaton. It obviously contains some of
-%unsatisfiability in the open transitions. In
-%Fig~\ref{schema:unsat-ot}, we display an unsatisfiable open transition
-%from the result of the CCS running example. It shows the case that the
-%top level transmits out the action from the PN2, formula $a.P$, as
-%this time only PN2 is working and C1 is performing action $a$ when
-%hole $P$ is also working. When matching this case against the second
-%synchronization 
-%vector of PN2, transmitting the behavior from hole $P$ to the higher
-%level, is used while it is obviously violate the guard of the
-%vector. So we can easily find the contradiction between the generated
-%predicate term $ra:152:1=l \!\land\! a=:ra:152:1$ and the guard
-%composed into the predicate $a \neq l$.
-\TODO{a more significant example, including state-variable assignements
-  ??}
+
 \begin{figure}[h]
-%$\begin{array}{@{}r@{}l@{}}
-%%{s0---a-->s1},   {---:hb:15:2-->},   (:ra:15:2 = act:sva:1:3)/\(:ra:152:1 = l)/\(a = :ra:152:1)/\(l!= a)/\(:hb:15:2 = y:sva:15:2)/\(:ra:15:2 = y:sva:15:2)/\(y:sva:15:2 != l)/\(:ra:1:3 = act:sva:1:3)
-%    ot  = &\openrule{\{0 \xrightarrow{a} 1\}, ~~\{\xrightarrow{:hb:15:2}\}, ~~:ra:15:2=act:sva:1:3 \\
-%    \OTland:ra:152:1=l \OTland a=:ra:152:1 \OTland a \neq l \OTland :hb:15:2 = y:sva:15:2 \\
-%    \OTland :ra:15:2 = y:sva:15:2  \OTland y:sva:15:2 \neq l \OTland :ra:1:3 = act:sva:1:3}
-%    {\ostate{00} \xrightarrow{:ra:1:3} \ostate{10}}\\
-%  \end{array}$
-%\caption{One of the unsatisfiable open transitions in CCS running example}  \label{schema:unsat-ot}
-%\end{figure}
-
-%{s0---delta-->s0},   {---:hb_P:12:1-->},   (:ra:11:1=l)/\(delta=:ra:11:1)/\(var_s0=0)/\(:hb_P:12:1=a1:sva_SV0:1:1)/\(:ra:1:1=a1:sva_SV0:1:1)/\(a1:sva_SV0:1:1!=delta(x)),   {var_s0 := 1}
-$\begin{array}{r@{}l}
-    ot  = &\openrule{\{s1 \xrightarrow{\OTvar{fail(false)}} s1, t1 \xrightarrow{\OTvar{resume(true)}} t0\}, ~~\{\xrightarrow{hb}\},~~\OTvar{fail(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
-    \OTland \OTvar{resume(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland \OTvar{hb}=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\OTland \OTvar{v}=\OTvar{\underline{fail}}\OTland \OTvar{b}_1 = \OTvar{b}_2\\
-    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
+\begin{mathpar}
+    \openrule{\{s1 \xrightarrow{\OTvar{fail(false)}} s1, t1 \xrightarrow{\OTvar{resume(true)}} t0\}, ~~\{\xrightarrow{hb}\},~~\OTvar{fail(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
+    \OTland \OTvar{resume(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland \OTvar{hb}=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\OTland \OTvar{v}=\OTvar{\underline{fail}}\OTland \OTvar{b}_1=\OTvar{b}_2\\
+    \OTland \OTvar{(}\OTvar{b}_1\lor\OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
     	   {\ostate{s1,t1} \xrightarrow{\OTvar{v}} \ostate{s1,t0}}\\
-  \end{array}$
+  \end{mathpar}
 \caption{One of the unsatisfiable open transitions in FailureTimer}  \label{schema:unsat-ot}
@@
 from the result of our example. It shows the case where
-the failure controller performs a ``$resume$'' action, while the timer
-executes a ``$start$''. The chosen synchronization
-vector does not match with these actions, as appears in the predicate
-fragment ``$\OTvar{resume(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}$''.
+the failure controller performs a ``$fail$'' action, while the timer
+executes a ``$resume$''. The chosen synchronization
+vector (SV0) does not match with these actions, as shown the predicate
+fragment ``resume(true)=start($b_2$)''.
 
@@
 or ``unsat''. The result "unsat" in the output is just what we expected.
+% as appears in the ``unsat'' proof generated by Z3 in which ``\{= ?x66 ?x70\}'' is shown to be false (see Fig. \ref{schema:smt-lib})
 
@@
 \paragraph{Translating assignments into predicate terms}
-\TODO{Only if we have it in the example...}
+State variable assignments that were collected during the open
+automaton are used when generating the SMTlib asserts (see
+appendix~\ref{appendix:translating-assignments}). This appears in
+Fig.~\ref{schema:smt-lib} in line 10, that encodes possible values of
+the variable $t$ of the timer.
 
@@
 \subsection{Result of the running example}
-\label{section:full-result}
+\label{section:resultOA}
 
@@
 get only 11 results left; the resulting open automaton is shown in
-Fig. ~\ref{schema:full-result}, together with its open transitions.
+Fig. ~\ref{schema:resultOA}, together with its open transitions.
 
@@
 result that we showed in the bottom part of
-Fig.~\ref{schema:lotos-result} is not the one generated by the algorithm,
+Fig.~\ref{schema:resultOA} is not the one generated by the algorithm,
 because the original one contains many intermediate
@@
 
-These are organized in th efollowing way:
+These are organized in the following way:
 
@@
 \item[B] Variable managment
-\item[C] Translation to SMTlib input language
+\item[C] Algebra presentations
 \item[D] Well-formness and typing of expressions
-\item[E]
+\item[E] Translation to SMTlib input language
+\item[F] Full output for our use-case
 
@@
 
-% \section{More details on the generation algorithm}
-
 \section{Variable managment}
-\label{appendix:varaibles}
+\label{appendix:variables}
 The variables in each synchronisation vector are considered local: for
@@
 
-\section{Translation to SMTlib input language}
+\section{Algebra presentations}
+\label{appendix:algpresentations}
 In order to submit satisfiability problems to Z3 (for the predicates
@@
 
-\begin{table}\caption{\label{table:BIPalgebra}\leftline{Additional
+\begin{table}\caption{\label{table:BIPoperators}\leftline{Additional
       operator for the BIP algebra}}
@@
 
-\begin{table}\caption{\label{table:BIPalgebra}\leftline{Additional
+\begin{table}\caption{\label{table:CCSalgebra}\leftline{Additional
       sorts and operators for the CCS algebra}}
@@
 
-\section{Map to SMT-LIB language}
+\section{Translation to SMTlib input language}
+\label{appendix:mapsmt}
 The pNet elements, as defined above, can be full translated into
@@
 \paragraph{Translating assignments into predicate terms}
-
+\label{appendix:translating-assignments}
+\TODO{INCORRECT, to be rewritten}
 State-variable assignments are also treated as a part of the

### 2018-01-18 2017-Xudong-SMT/FM-2018-extended.tex
Minor: clean-up of notes Also reduced a bit more the space between figure captions and text (see the belowskip option of the caption package

@@
     aboveskip=4pt,
-    belowskip=-12pt,
+    belowskip=-18pt,
 ]{caption}
@@
 \newcommand{\noteEM}[2][color=blue!40, size=\tiny]{\todo[#1]{{\bf Eric: } {#2}}}
-\newcommand{\noteInSB}[2][inline,color=green!40]{\todo[#1]{{\bf Note: } {#2}}}
+\newcommand{\noteInSB}[2][inline,color=green!40]{\todo[#1]{{\bf Simon: } {#2}}}
 
@@
 reset, unless a resumption is registered within $\mathrm{Max}$ time
-units.\noteSB{Here, it would be nice to explain the role of the
-  singleton connectors, but that would take too much space. AGREED}
+units.
 
@@
   \includegraphics[width=0.9\columnwidth]{XFIG/FailureTimerPNET}
-  \caption{pNet encoding of the FailureTimer architecture
-  \noteEM[inline]{Was a little too small for me, my eyes are getting tired...}}
+  \caption{pNet encoding of the Failure Monitor architecture}
   \label{schema:ArchFailure:pNet}
@@
 
-\noteSB{SV2 should not be closed;\\SV0, SV1: $\cup \rightarrow \lor$... DONE}
-%\hl{%
-%
 Figure~\ref{schema:ArchFailure:pNet} shows a pNet encoding of the
@@
 connector~\cite{BliSif10-causal-fmsd}.
-%
-%}
-\noteSB{
-%
-  Eric, could you please check my pNet terminology in this paragraph?
-%
-}
-\noteEM{Done, it's ok.}
 %

### 2018-01-18 2017-Xudong-SMT/FM-2018-extended.tex
Modify the TMAX.
TMAX from IntLiteral to Variable.
Then the transitions changed.

@@
 \begin{mathpar}
-    \openrule{\{s1 \xrightarrow{\OTvar{fail(false)}} s1, t1 \xrightarrow{\OTvar{resume(true)}} t0\}, ~~\{\xrightarrow{hb}\},~~\OTvar{fail(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
-    \OTland \OTvar{resume(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland \OTvar{hb}=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\OTland \OTvar{v}=\OTvar{\underline{fail}}\OTland \OTvar{b}_1=\OTvar{b}_2\\
-    \OTland \OTvar{(}\OTvar{b}_1\lor\OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
-    	   {\ostate{s1,t1} \xrightarrow{\OTvar{v}} \ostate{s1,t0}}\\
+    ot = \openrule{\{s1 \xrightarrow{fail(false)} s1, t1 \xrightarrow{resume(true)} t0\}, ~~\{\xrightarrow{hb}\},~~fail(false)=fail(b_1)\\
+    \OTland resume(true)=start(b_2)\OTland hb=fail(b_0)\OTland v=\underline{fail}\OTland b_1=b_2\\
+    \OTland (b_1\lor b_2) \Rightarrow b_0, ~~\{\}}
+    	   {\ostate{s1,t1} \xrightarrow{v} \ostate{s1,t0}}\\
   \end{mathpar}
@@
 \begin{lstlisting}[basicstyle=\scriptsize\ttfamily, frame=single]
-   {s0---fail(true)-->s1, t0---start(true)-->t1}, {---:hb_B:13:1-->},
-   (fail(true)=fail(b1:sva_SV0:1:1))/\(start(true)=start(b2:sva_SV0:1:1))
+	{s0---failure(true)-->s1, t0---start(true)-->t1},{---:hb_B:13:1-->},   
+	(failure(true)=failure(b1:sva_SV0:1:1))
+	/\(start(true)=start(b2:sva_SV0:1:1))
 	/\(:hb_B:13:1=fail(b0:sva_SV0:1:1))/\((b1:sva_SV0:1:1=b2:sva_SV0:1:1)
-   /\(~(b1:sva_SV0:1:1\/b2:sva_SV0:1:1)\/b0:sva_SV0:1:1))/\(_fail_=:ra:1:1),
-   {t := 4}
-OT ------------------------------------------------------------
+	/\(~(b1:sva_SV0:1:1\/b2:sva_SV0:1:1)\/b0:sva_SV0:1:1))
+	/\(_fail_=:ra:1:1),{t := Max}
+OT ---------------------------------------------------------------------------
 		<s0_t0>-----:ra:1:1----><s1_t1>
 
-   {s0---resume(false)-->s0, t0---resume(false)-->t0},   {---:hb_B:16:2-->},
-   (resume(false)=resume(b1:sva_SV1:1:2))/\(resume(false)=resume(b2:sva_SV1:1:2))
+	{s0---resume(false)-->s0, t0---resume(false)-->t0},{---:hb_B:16:2-->},   
+	(resume(false)=resume(b1:sva_SV1:1:2))
+	/\(resume(false)=resume(b2:sva_SV1:1:2))
 	/\(:hb_B:16:2=resume(b0:sva_SV1:1:2))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2)
-   /\(~(b1:sva_SV1:1:2\/b2:sva_SV1:1:2)\/b0:sva_SV1:1:2))/\(_resume_=:ra:1:2), {}
-OT ------------------------------------------------------------
+	/\(~(b1:sva_SV1:1:2\/b2:sva_SV1:1:2)\/b0:sva_SV1:1:2)
+	/\(_resume_=:ra:1:2),{}
+OT ---------------------------------------------------------------------------
 	<s0_t0>-----:ra:1:2----><s0_t0>
 
-   {},   {---:hb_B:118:6-->},   (:hb_B:118:6=finish)/\(finish=:ra:1:6),  {}
-OT ------------------------------------------------------------
+	{},{---:hb_B:118:6-->},(:hb_B:118:6=finish)/\(finish=:ra:1:6),{}
+OT ---------------------------------------------------------------------------
 	<s0_t0>-----:ra:1:6----><s0_t0>
 
-   {s1---fail(false)-->s1, t1---start(false)-->t1},   {---:hb_B:13:1-->},
-   (fail(false)=fail(b1:sva_SV0:1:1))/\(start(false)=start(b2:sva_SV0:1:1))
+	{s1---failure(false)-->s1, t1---start(false)-->t1},{---:hb_B:13:1-->},   
+	(failure(false)=failure(b1:sva_SV0:1:1))
+	/\(start(false)=start(b2:sva_SV0:1:1))
 	/\(:hb_B:13:1=fail(b0:sva_SV0:1:1))/\((b1:sva_SV0:1:1=b2:sva_SV0:1:1)
-   /\(~(b1:sva_SV0:1:1\/b2:sva_SV0:1:1)\/b0:sva_SV0:1:1))/\(_fail_=:ra:1:1), {}
-OT ------------------------------------------------------------
+	/\(~(b1:sva_SV0:1:1\/b2:sva_SV0:1:1)\/b0:sva_SV0:1:1))
+	/\(_fail_=:ra:1:1),{}
+OT ---------------------------------------------------------------------------
 	<s1_t1>-----:ra:1:1----><s1_t1>
 
-   {s1---resume(true)-->s0, t1---resume(true)-->t0},   {---:hb_B:16:2-->},
-   (resume(true)=resume(b1:sva_SV1:1:2))/\(resume(true)=resume(b2:sva_SV1:1:2))
+	{s1---resume(true)-->s0, t1---resume(true)-->t0},{---:hb_B:16:2-->},   
+	(resume(true)=resume(b1:sva_SV1:1:2))
+	/\(resume(true)=resume(b2:sva_SV1:1:2))
 	/\(:hb_B:16:2=resume(b0:sva_SV1:1:2))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2)
-   /\(~(b1:sva_SV1:1:2\/b2:sva_SV1:1:2)\/b0:sva_SV1:1:2))/\(_resume_=:ra:1:2), {}
-OT ------------------------------------------------------------
+	/\(~(b1:sva_SV1:1:2\/b2:sva_SV1:1:2)\/b0:sva_SV1:1:2))
+	/\(_resume_=:ra:1:2),{}
+OT ---------------------------------------------------------------------------
 	<s1_t1>-----:ra:1:2----><s0_t0>
 
-   {t1---tick-->t1},   {},   (t!=0)/\(_tick_=:ra:1:3),   {t := (t-1)}
-OT ------------------------------------------------------------
+	{t1---tick-->t1},{},(t>0)/\(tick=:ra:1:3),{t := (t-1)}
+OT ---------------------------------------------------------------------------
 	<s1_t1>-----:ra:1:3----><s1_t1>
 
-   {},  {---:hb_B:118:6-->},  (:hb_B:118:6=finish)/\(finish=:ra:1:6),  {}
-OT ------------------------------------------------------------
+	{},{---:hb_B:118:6-->},(:hb_B:118:6=finish)/\(finish=:ra:1:6),{}
+OT ---------------------------------------------------------------------------
 	<s1_t1>-----:ra:1:6----><s1_t1>
 
-   {s1---timeout-->s2, t1---timeout-->t0},  {},  (t=0)/\(ask=:ra:1:4),  {}
-OT ------------------------------------------------------------
+	{s1---timeout-->s2, t1---timeout-->t0}, {},(t=0)/\(ask=:ra:1:4),{}
+OT ---------------------------------------------------------------------------
 	<s1_t1>-----:ra:1:4----><s2_t0>
 
-   {s2---resume(false)-->s2, t0---resume(false)-->t0},   {---:hb_B:16:2-->},
-   (resume(false)=resume(b1:sva_SV1:1:2))/\(resume(false)=resume(b2:sva_SV1:1:2))
+	{s2---resume(false)-->s2, t0---resume(false)-->t0},{---:hb_B:16:2-->},   
+	(resume(false)=resume(b1:sva_SV1:1:2))
+	/\(resume(false)=resume(b2:sva_SV1:1:2))
 	/\(:hb_B:16:2=resume(b0:sva_SV1:1:2))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2)
-   /\(~(b1:sva_SV1:1:2\/b2:sva_SV1:1:2)\/b0:sva_SV1:1:2))/\(_resume_=:ra:1:2),
-   {}
-OT ------------------------------------------------------------
+	/\(~(b1:sva_SV1:1:2\/b2:sva_SV1:1:2)\/b0:sva_SV1:1:2))
+	/\(_resume_=:ra:1:2),{}
+OT ---------------------------------------------------------------------------
 	<s2_t0>-----:ra:1:2----><s2_t0>
 
-   {s2---reset-->s0},   {},   (reset=:ra:1:5),   {}
-OT ----------------------------------------------------------
+	{s2---reset-->s0},{},(reset=:ra:1:5),{}
+OT ---------------------------------------------------------------------------
 	<s2_t0>-----:ra:1:5----><s0_t0>
 
-   {},  {---:hb_B:118:6-->},  (:hb_B:118:6=finish)/\(finish=:ra:1:6),  {}
-OT ------------------------------------------------------------
+	{},{---:hb_B:118:6-->},(:hb_B:118:6=finish)/\(finish=:ra:1:6),{}
+OT ---------------------------------------------------------------------------
 	<s2_t0>-----:ra:1:6----><s2_t0>
@@
     \OTland \OTvar{start(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland hb_1=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\OTland v_1=\OTvar{\underline{fail}}\OTland \OTvar{b}_1 = \OTvar{b}_2
-    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
+    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{t := Max\}}
     	   {\ostate{s0,t0} \xrightarrow{v_1} \ostate{s1,t1}}\\
@@
     \OTland \OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_2=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\OTland v_2=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
-    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{t := 4\}}
+    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
     	    {\ostate{s0,t0} \xrightarrow{v_2} \ostate{s0,t0}}\\
@@
 $\begin{array}{r@{}l}
-    ot_6  = &\openrule{\{t1 \xrightarrow{\OTvar{tick}} t1\}, ~~\{\},~~t\neq 0\OTland v_6=\OTvar{\underline{tick}}, ~~\{t := t-1 \}}
+    ot_6  = &\openrule{\{t1 \xrightarrow{\OTvar{tick}} t1\}, ~~\{\},~~t\neq 0\OTland v_6=\OTvar{tick}, ~~\{t := t-1 \}}
     	   {\ostate{s1,t1} \xrightarrow{v_6} \ostate{s1,t0}}\\

### 2018-01-18 2017-Xudong-SMT/FM-2018-extended.tex
Additional example of priority in Section 3 Moved the figures a bit in Section 5

--- 2018-01-18 2017-Xudong-SMT/FM-2018-extended.tex
@@
 code, executable by linking with one of the dedicated engines, which
-implement the BIP operational semantics~\cite{BliSif08-acp-tc}.  This
+implement the BIP operational semantics~\cite{BarBliu15-offer-scico}.  This
 approach ensures that any property, shown to hold on a given BIP
@@
 the set of possible interactions\mdash narrow the choice among the
-enabled interactions at any given execution round.  The default priority is the
+enabled interactions at any given round.  The default priority is the
 so-called \emph{maximal progress}, whereby among any two interactions
@@
 $\NameCtrl.\PortFail$ are enabled.
+%
+Adding priorities $\NameOprnd.\PortFinish < \NameCtrl.\PortReset$ and
+$\NameOprnd.\PortFinish < \NameOprnd.\PortResume$, ensures that, after
+a failure, the operation performed by $\NameOprnd$ cannot finish
+unless it is explicitly resumed or the system is reset.
 
@@
 reset, unless a resumption is registered within $\mathrm{Max}$ time
-units.
+units (more details in Sect.~\ref{section:resultOA}).
 
@@
 %
-Although, for the sake of brevity, this encoding does not translate
-the maximal progress priority, it can be easily extended to do so, by
-introducing an additional Boolean variable for each relevant port.
+Although, for the sake of brevity, we omit priorities from the
+encoding, this can be easily achieved, by introducing additional
+Boolean variables for relevant ports~\cite{BarBliu15-offer-scico}.
 
@@
 
-\begin{figure}[h]
-\begin{mathpar}
-    \openrule{\{s1 \xrightarrow{\OTvar{fail(false)}} s1, t1 \xrightarrow{\OTvar{resume(true)}} t0\}, ~~\{\xrightarrow{hb}\},~~\OTvar{fail(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
-    \OTland \OTvar{resume(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland \OTvar{hb}=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\OTland \OTvar{v}=\OTvar{\underline{fail}}\OTland \OTvar{b}_1=\OTvar{b}_2\\
-    \OTland \OTvar{(}\OTvar{b}_1\lor\OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
-    	   {\ostate{s1,t1} \xrightarrow{\OTvar{v}} \ostate{s1,t0}}\\
-  \end{mathpar}
-\caption{One of the unsatisfiable open transitions in FailureTimer}  \label{schema:unsat-ot}
-\end{figure}
-
 Our matching/filtering strategy builds some transitions where
@@
 
+\begin{figure}[t]
+\begin{mathpar}
+    \openrule{\{s1 \xrightarrow{\OTvar{fail(false)}} s1, t1 \xrightarrow{\OTvar{resume(true)}} t0\}, ~~\{\xrightarrow{hb}\},~~\OTvar{fail(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
+    \OTland \OTvar{resume(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland \OTvar{hb}=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\OTland \OTvar{v}=\OTvar{\underline{fail}}\OTland \OTvar{b}_1=\OTvar{b}_2\\
+    \OTland \OTvar{(}\OTvar{b}_1\lor\OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
+    	   {\ostate{s1,t1} \xrightarrow{\OTvar{v}} \ostate{s1,t0}}
+  \end{mathpar}
+\caption{One of the unsatisfiable open transitions in FailureTimer}  \label{schema:unsat-ot}
+\end{figure}
+
 Checking satisfiability requires some symbolic computation
@@
 the solver can use specific properties of each action algebra.
-
-\begin{figure}[t]
-  %  \centerline{\includegraphics[width=12cm]{XFIG/SMTLIB2}}
-    \centerline{\includegraphics[width=\linewidth]{XFIG/SMTLIB3}}
-  \caption{The input of the Z3 solver in SMT-LIB language and the output result}  \label{schema:smt-lib}
-\end{figure}
-
-%% \begin{figure}[t]
-%%   \centerline{\includegraphics[width=10cm]{XFIG/Interaction}}
-%%   \caption{The architecture of the interaction between pNet API and Z3}  \label{schema:interaction}
-%% \end{figure}
 
@@
 
-Fig.~\ref{schema:smt-lib} shows the translation of the
+Figure~\ref{schema:smt-lib} shows the translation of the
 transition of Fig.~\ref{schema:unsat-ot}
@@
 % as appears in the ``unsat'' proof generated by Z3 in which ``\{= ?x66 ?x70\}'' is shown to be false (see Fig. \ref{schema:smt-lib})
+
+\begin{figure}[t]
+  %  \centerline{\includegraphics[width=12cm]{XFIG/SMTLIB2}}
+    \centerline{\includegraphics[width=\linewidth]{XFIG/SMTLIB3}}
+  \caption{The input of the Z3 solver in SMT-LIB language and the output result}  \label{schema:smt-lib}
+\end{figure}
+
+%% \begin{figure}[t]
+%%   \centerline{\includegraphics[width=10cm]{XFIG/Interaction}}
+%%   \caption{The architecture of the interaction between pNet API and Z3}  \label{schema:interaction}
+%% \end{figure}
 
@@
 
-\subsection{Result of the running example}
+\subsection{Result for the running example}
 \label{section:resultOA}
@@
   \centerline{\includegraphics[width=12cm]{XFIG/FailureTimerOA}}
-   \caption{Open Automaton}  \label{schema:resultOA}
+  \caption{Open Automaton for the Failure Monitor architecture}
+  \label{schema:resultOA}
 \end{figure}

### 2018-01-18 2017-Xudong-SMT/FM-2018-extended.tex

--- 2018-01-18 2017-Xudong-SMT/FM-2018-extended.tex
@@
 
-\begin{figure}[h]
-\begin{mathpar}
-    ot = \openrule{\{s1 \xrightarrow{fail(false)} s1, t1 \xrightarrow{resume(true)} t0\}, ~~\{\xrightarrow{hb}\},~~fail(false)=fail(b_1)\\
-    \OTland resume(true)=start(b_2)\OTland hb=fail(b_0)\OTland v=\underline{fail}\OTland b_1=b_2\\
-    \OTland (b_1\lor b_2) \Rightarrow b_0, ~~\{\}}
-    	   {\ostate{s1,t1} \xrightarrow{v} \ostate{s1,t0}}\\
-  \end{mathpar}
-\caption{One of the unsatisfiable open transitions in FailureTimer}  \label{schema:unsat-ot}
-\end{figure}
-
 Our matching/filtering strategy builds some transitions where
@@
 
+\begin{figure}[t]
+\begin{mathpar}
+    ot = \openrule{\{s1 \xrightarrow{fail(false)} s1, t1 \xrightarrow{resume(true)} t0\}, ~~\{\xrightarrow{hb}\},~~fail(false)=fail(b_1)\\
+    \OTland resume(true)=start(b_2)\OTland hb=fail(b_0)\OTland v=\underline{fail}\OTland b_1=b_2\\
+    \OTland (b_1\lor b_2) \Rightarrow b_0, ~~\{\}}
+    	   {\ostate{s1,t1} \xrightarrow{v} \ostate{s1,t0}}\\
+  \end{mathpar}
+\caption{One of the unsatisfiable open transitions in FailureTimer}  \label{schema:unsat-ot}
+\end{figure}
+
 Checking satisfiability requires some symbolic computation

### 2018-01-18 2017-Xudong-SMT/FM-2018-extended.tex
Added a reference for CTL (Baier & Katoen) Formulated and formalised two properties in Section 5.4 (Justification of correctness still missing)

@@
   architectures.  Future work may include automatic synthesis of
-  architectures from, \eg CTL or a similar logic. 
+  architectures from, \eg[,] CTL~\cite{BaierKatoen2008} formulae.
 %
@@
 
-On this example, the tool builds 184 open
-transitions, out of which 173 are detected unsatisfiable by Z3, we
-get only 11 results left; the resulting open automaton is shown in
-Fig. ~\ref{schema:resultOA}, together with its open transitions.
+For this example, the tool builds 184 open transitions, whereof 173
+are detected unsatisfiable by Z3.  The resulting open automaton, with
+3 reachable global states (out of the possible 6) and 11 open
+transitions, is shown in Fig.~\ref{schema:resultOA}.
+
+\begin{figure}[t]
+  \centerline{\includegraphics[width=12cm]{XFIG/FailureTimerOA}}
+  \caption{Open Automaton for the Failure Monitor architecture}
+  \label{schema:resultOA}
+\end{figure}
 
@@
 predicate.
-
-Remark that only 3 global states out of the possible 6 are reachable
-here. \TODO{it would be good to express here maybe 2 properties of the
+%
+Notice, however that the loop transitions
+$\underline{\mathit{resume}}$ in states $\ostate{s0,t0}$ and
+$\ostate{s2,t0}$, corresponding, respectively, to open transitions
+$ot_2$ and $ot_9$ in Fig.~\ref{schema:ots} of
+App.~\ref{appendix:fullOutput}, involve $\OTvar{resume(false)}$ from
+the two pLTS, \ie only the hole, corresponding to the operand
+component of the Failure Monitor architecture, executes $\PortResume$.
+
+Failure Monitor enforces 1)~the safety property \emph{``the
+  system reset never happens, unless asked for by a timeout
+  following a failure''}, formalised in CTL by
+%
+\[
+\varphi \land \mathtt{AG} (\PortReset \rightarrow \varphi)\,,
+\quad\text{where}\quad
+%
+\varphi = \mathtt{A} [\lnot \PortReset\ \mathtt{W}\ \PortAsk]
+\land \mathtt{A} [\lnot \PortAsk\ \mathtt{W}\ \PortFail]
+\]
+%
+($\mathtt{W}$ being the \emph{weak until} operator) and 2)~the
+liveness property \emph{``a reset will be fired when asked for by
+  a timeout''}:
+%
+$\mathtt{AG}(\PortAsk \rightarrow \mathtt{AF}\ \PortReset)$.
+%
+
+\TODO{it would be good to express here maybe 2 properties of the
   architecture, maybe one taken fromm the original study, and another
   one involving the timer data (number of ticks ?)}
-
-\begin{figure}[t]
-  \centerline{\includegraphics[width=12cm]{XFIG/FailureTimerOA}}
-  \caption{Open Automaton for the Failure Monitor architecture}
-  \label{schema:resultOA}
-\end{figure}
 
@@
     ot_2  = &\openrule{\{s0 \xrightarrow{\OTvar{resume(false)}} s0, t0 \xrightarrow{\OTvar{resume(false)}} t0\}, ~~\{\xrightarrow{hb_2}\},~~\OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_1\OTvar{)}\\
-    \OTland \OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_2=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\OTland v_2=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
+    \OTland \OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_2=\OTvar{resume(}\OTvar{b}_0\OTvar{)}\OTland v_2=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
     \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
@@
     ot_9  = &\openrule{\{s2 \xrightarrow{\OTvar{resume(false)}} s2, t0 \xrightarrow{\OTvar{resume(false)}} t0\}, ~~\{\xrightarrow{hb_9}\},~~\OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_1\OTvar{)}\\
-    \OTland \OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_9=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\OTland v_9=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
+    \OTland \OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_9=\OTvar{resume(}\OTvar{b}_0\OTvar{)}\OTland v_9=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
     \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}

### 2018-01-19 2017-Xudong-SMT/FM-2018-extended.tex
Word spelling.

--- 2018-01-18 2017-Xudong-SMT/FM-2018-extended.tex
@@
 terms of so-called ``Open Automata''. This allows to check properties of
-such systems in a compositionnal manner. 
+such systems in a compositional manner. 
 We implement an algorithm computing this semantics,
@@
 ESA microsatellites. We use pNets to encode BIP architectures,
-extended with explicite data in synchronisations, and we compute their
+extended with explicit data in synchronizations, and we compute their
 open automaton semantics. This automaton may then be used to prove
@@
       combination of all possible (symbolic) behaviors; on the other hand
-      the symbolic reasonning part, specificaly here using an SMT
+      the symbolic reasoning part, specifically here using an SMT
       engine to check the
@@
 CubETH nanosatellite on-board software
-case-study~\cite{CubETH-case-study} realised using BIP.  BIP
-(Behaviour-Interaction-Priority)~\cite{bip} is a framework for the
+case-study~\cite{CubETH-case-study} realized using BIP.  BIP
+(behavior-Interaction-Priority)~\cite{bip} is a framework for the
 component-based design of concurrent software and systems.  In
@@
 code, executable by linking with one of the dedicated engines, which
-implement the BIP operational semantics~\cite{BarBliu15-offer-scico}.  This
+implement the BIP operational semantics~\cite{BliSif08-acp-tc}.  This
 approach ensures that any property, shown to hold on a given BIP
@@
 Architectures can be viewed as operators transforming BIP models.
-They formalise design patterns, which enforce global properties
-characterising the coordination among the components of the system.
+They formalize design patterns, which enforce global properties
+characterizing the coordination among the components of the system.
 The architecture-based design process in BIP takes as input a set of
@@
 coordinator components and modifying the connectors that define
-synchronisation patterns among ports of components.
+synchronization patterns among ports of components.
 In~\cite{AttieBBJS16-architectures-faoc}, it was shown that
@@
 $\NameTimer$\mdash are standard BIP components insofar as they also
-have their \emph{behaviour} specified by finite automata extended with
+have their \emph{behavior} specified by finite automata extended with
 local data variables.  Transitions of these automata are labelled with
@@
 $\NameCtrl.\PortFail$ are enabled.
-%
-Adding priorities $\NameOprnd.\PortFinish < \NameCtrl.\PortReset$ and
-$\NameOprnd.\PortFinish < \NameOprnd.\PortResume$, ensures that, after
-a failure, the operation performed by $\NameOprnd$ cannot finish
-unless it is explicitly resumed or the system is reset.
 
@@
 reset, unless a resumption is registered within $\mathrm{Max}$ time
-units (more details in Sect.~\ref{section:resultOA}).
+units.
 
@@
 component\mdash as a hole; connectors of the BIP model are encoded as
-synchronisation vectors.  Each connector that does not involve
-triggers is trivially encoded by a synchronisation vector comprising
+synchronization vectors.  Each connector that does not involve
+triggers is trivially encoded by a synchronization vector comprising
 the same ports.  In order to encode the semantics of the connectors
@@
 \goesto{\PortFail(\false)} \cstate{2}$), 3)~add to the corresponding
-synchronisation vectors the Boolean predicate encoding the connector
+synchronization vectors the Boolean predicate encoding the connector
 structure.  For example, $SV0$ encodes the connector discussed above:
@@
 %
-Although, for the sake of brevity, we omit priorities from the
-encoding, this can be easily achieved, by introducing additional
-Boolean variables for relevant ports~\cite{BarBliu15-offer-scico}.
+Although, for the sake of brevity, this encoding does not translate
+the maximal progress priority, it can be easily extended to do so, by
+introducing an additional Boolean variable for each relevant port.
 
@@
 Last, at the root of the pNet, the predicate of each OT is translated
-into SMTlib assertions, and checked for satifiability. Unsatisfiable
+into SMTlib assertions, and checked for satisfiability. Unsatisfiable
 OTs are pruned, and the final open automaton is computed as the set of
@@
 \paragraph{Combining:}
-The combining method enumerate all the possible behaviours of the
+The combining method enumerate all the possible behaviors of the
 subnets, as all the possible combinations of their open transitions.
@@
 \paragraph{Matching:}
-The next step, for each synchronisation vector, and each possible
-combination of behaviour of the subnets as generated by the \emph
+The next step, for each synchronization vector, and each possible
+combination of behavior of the subnets as generated by the \emph
 {Combining} method, consists in building the combined predicate,
@@
   \item if some subnet is marked as inactive in the vector, and the
-    chosen combinaison has an active behaviour at this position,
+    chosen combination has an active behavior at this position,
   \item if some subnet action expression in the vector does not match (by
-    pattern-matching) the corresponding behaviour $C_n$,
+    pattern-matching) the corresponding behavior $C_n$,
   \item or if the whole set of active subnet actions in the vector
@@
 apply only the simplest filter inside the \emph{Matching} method. All
-the rest will be checked later, using the satisfiability ckeck in the
+the rest will be checked later, using the satisfiability check in the
 SMT engine.
@@
 
+\begin{figure}[h]
+\begin{mathpar}
+    ot = \openrule{\{s1 \xrightarrow{fail(false)} s1, t1 \xrightarrow{resume(true)} t0\}, ~~\{\xrightarrow{hb}\},~~fail(false)=fail(b_1)\\
+    \OTland resume(true)=start(b_2)\OTland hb=fail(b_0)\OTland v=\underline{fail}\OTland b_1=b_2\\
+    \OTland (b_1\lor b_2) \Rightarrow b_0, ~~\{\}}
+    	   {\ostate{s1,t1} \xrightarrow{v} \ostate{s1,t0}}\\
+  \end{mathpar}
+\caption{One of the unsatisfiable open transitions in FailureTimer}  \label{schema:unsat-ot}
+\end{figure}
+
 Our matching/filtering strategy builds some transitions where
@@
 
-\begin{figure}[t]
-\begin{mathpar}
-    ot = \openrule{\{s1 \xrightarrow{fail(false)} s1, t1 \xrightarrow{resume(true)} t0\}, ~~\{\xrightarrow{hb}\},~~fail(false)=fail(b_1)\\
-    \OTland resume(true)=start(b_2)\OTland hb=fail(b_0)\OTland v=\underline{fail}\OTland b_1=b_2\\
-    \OTland (b_1\lor b_2) \Rightarrow b_0, ~~\{\}}
-    	   {\ostate{s1,t1} \xrightarrow{v} \ostate{s1,t0}}\\
-  \end{mathpar}
-\caption{One of the unsatisfiable open transitions in FailureTimer}  \label{schema:unsat-ot}
-\end{figure}
-
 Checking satisfiability requires some symbolic computation
@@
 the solver can use specific properties of each action algebra.
+
+\begin{figure}[t]
+  %  \centerline{\includegraphics[width=12cm]{XFIG/SMTLIB2}}
+    \centerline{\includegraphics[width=\linewidth]{XFIG/SMTLIB3}}
+  \caption{The input of the Z3 solver in SMT-LIB language and the output result}  \label{schema:smt-lib}
+\end{figure}
+
+%% \begin{figure}[t]
+%%   \centerline{\includegraphics[width=10cm]{XFIG/Interaction}}
+%%   \caption{The architecture of the interaction between pNet API and Z3}  \label{schema:interaction}
+%% \end{figure}
 
@@
 
-Figure~\ref{schema:smt-lib} shows the translation of the
+Fig.~\ref{schema:smt-lib} shows the translation of the
 transition of Fig.~\ref{schema:unsat-ot}
@@
 % as appears in the ``unsat'' proof generated by Z3 in which ``\{= ?x66 ?x70\}'' is shown to be false (see Fig. \ref{schema:smt-lib})
-
-\begin{figure}[t]
-  %  \centerline{\includegraphics[width=12cm]{XFIG/SMTLIB2}}
-    \centerline{\includegraphics[width=\linewidth]{XFIG/SMTLIB3}}
-  \caption{The input of the Z3 solver in SMT-LIB language and the output result}  \label{schema:smt-lib}
-\end{figure}
-
-%% \begin{figure}[t]
-%%   \centerline{\includegraphics[width=10cm]{XFIG/Interaction}}
-%%   \caption{The architecture of the interaction between pNet API and Z3}  \label{schema:interaction}
-%% \end{figure}
 
@@
 
-\subsection{Result for the running example}
+\subsection{Result of the running example}
 \label{section:resultOA}
@@
    \centerline{\includegraphics[width=12cm]{XFIG/FailureTimerOA}}
-  \caption{Open Automaton for the Failure Monitor architecture}
-  \label{schema:resultOA}
+   \caption{Open Automaton}  \label{schema:resultOA}
  \end{figure}
@@
 pLTS transitions on these states, and compose them with actions of
-holes using synchronisation vectors. %The pNet
+holes using synchronization vectors. %The pNet
 %structure does not appear in the open-automaton, only the
@@
 \label{appendix:variables}
-The variables in each synchronisation vector are considered local: for
+The variables in each synchronization vector are considered local: for
 a given pNet expression, we must have fresh local variables for each
@@
   resulting actions of transitions, variables created during the cloning
-  of synchronisation vectors.
+  of synchronization vectors.
 \end{itemize}
@@
 Let $\mylangle\overline{\pNet},\overline{S},\symb{SV}_k^{k\in K} \myrangle$
-be a pNet. Choose a synchronisation vector $SV=clone(SV_k) ={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v' \, ,G_k $, for $k\in K$. The
+be a pNet. Choose a synchronization vector $SV=clone(SV_k) ={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v' \, ,G_k $, for $k\in K$. The
 predicate $\Pred$ relating

### 2018-01-19 2017-Xudong-SMT/FM-2018-extended.tex

@@
 
-\subsection{Result of the running example}
+\subsection{Result for the running example}
 \label{section:resultOA}
 
-On this example, the tool builds 184 open
-transitions, out of which 173 are detected unsatisfiable by Z3, we
-get only 11 results left; the resulting open automaton is shown in
-Fig. ~\ref{schema:resultOA}, together with its open transitions.
+For this example, the tool builds 184 open transitions, whereof 173
+are detected unsatisfiable by Z3.  The resulting open automaton, with
+3 reachable global states (out of the possible 6) and 11 open
+transitions, is shown in Fig.~\ref{schema:resultOA}.
+
+\begin{figure}[t]
+  \centerline{\includegraphics[width=12cm]{XFIG/FailureTimerOA}}
+  \caption{Open Automaton for the Failure Monitor architecture}
+  \label{schema:resultOA}
+\end{figure}
 
@@
 predicate.
-
-Remark that only 3 global states out of the possible 6 are reachable
-here. \TODO{it would be good to express here maybe 2 properties of the
+%
+Notice, however that the loop transitions
+$\underline{\mathit{resume}}$ in states $\ostate{s0,t0}$ and
+$\ostate{s2,t0}$, corresponding, respectively, to open transitions
+$ot_2$ and $ot_9$ in Fig.~\ref{schema:ots} of
+App.~\ref{appendix:fullOutput}, involve $\OTvar{resume(false)}$ from
+the two pLTS, \ie only the hole, corresponding to the operand
+component of the Failure Monitor architecture, executes $\PortResume$.
+
+Failure Monitor enforces 1)~the safety property \emph{``the
+  system reset never happens, unless asked for by a timeout
+  following a failure''}, formalised in CTL by
+%
+\[
+\varphi \land \mathtt{AG} (\PortReset \rightarrow \varphi)\,,
+\quad\text{where}\quad
+%
+\varphi = \mathtt{A} [\lnot \PortReset\ \mathtt{W}\ \PortAsk]
+\land \mathtt{A} [\lnot \PortAsk\ \mathtt{W}\ \PortFail]
+\]
+%
+($\mathtt{W}$ being the \emph{weak until} operator) and 2)~the
+liveness property \emph{``a reset will be fired when asked for by
+  a timeout''}:
+%
+$\mathtt{AG}(\PortAsk \rightarrow \mathtt{AF}\ \PortReset)$.
+%
+
+\TODO{it would be good to express here maybe 2 properties of the
   architecture, maybe one taken fromm the original study, and another
   one involving the timer data (number of ticks ?)}
-
-\begin{figure}[t]
-   \centerline{\includegraphics[width=12cm]{XFIG/FailureTimerOA}}
-   \caption{Open Automaton}  \label{schema:resultOA}
- \end{figure}
 

### 2018-01-19 2017-Xudong-SMT/FM-2018-extended.tex
Correct some spelling.

--- 2018-01-18 2017-Xudong-SMT/FM-2018-extended.tex
@@
   \item if some subnet is marked as inactive in the vector, and the
-    chosen combinaison has an active behaviour at this position,
+    chosen combination has an active behaviour at this position,
   \item if some subnet action expression in the vector does not match (by
@@
 \paragraph{Translation of Action algebra presentation}
-In appendix \ref{appendix:mapsmt} we define formaly a condition of
+In appendix \ref{appendix:mapsmt} we define formally a condition of
 well-formness of an algebra presentation, and its translation into
@@
 
-In appendix \ref{appendix:mapsmt} we formaly define the translation of each
+In appendix \ref{appendix:mapsmt} we formally define the translation of each
 open transition, including:
@@
 - check well-formness and correct typing of expressions
-- translate the predicate into a conjunction of assertations
+- translate the predicate into a conjunction of assertions
 - if present in the source state, translate the state-variable
@@
 \TODO{it would be good to express here maybe 2 properties of the
-  architecture, maybe one taken fromm the original study, and another
+  architecture, maybe one taken from the original study, and another
   one involving the timer data (number of ticks ?)}
@@
 Our intention is to publish as a research report, before final publication, an
-extended version containing all technical detials, proofs, and more examples.
+extended version containing all technical details, proofs, and more examples.
 
@@
 \item[A] pNet semantic rules
-\item[B] Variable managment
+\item[B] Variable management
 \item[C] Algebra presentations
@@
 
-\section{Variable managment}
+\section{Variable management}
 \label{appendix:variables}
@@
 \item $Const(pnet)$: Constants from the pLTSs (controllers) transitions: these are
-  new constant constructors, usualy of sort Action, local to an
+  new constant constructors, usually of sort Action, local to an
   instance of a controller. The pNet definition requires that all
@@
 SMT-LIB language, but there are a number of differences in the
-structure of the models/langages, so the translation is not trivial.
+structure of the models/languages, so the translation is not trivial.
 
@@
 - for each SCC in this graph, construct: 
-  dataype-declaration = TrPresentation (Pres, SCC)
+  datatype-declaration = TrPresentation (Pres, SCC)
 - for each other operator op in Ops, construct:
@@
   rules; and $BuildFunInstance$ use these argument types as suffixes
-  to disembiguate 
+  to disambiguate 
 \end{itemize}
@@
 
-\TODO{Need to add an exemple with 2 instances of FUN}
+\TODO{Need to add an example with 2 instances of FUN}
 
@@
 all variables used in OT.
-\item check that all pLTS labels (action, guard, assignement) in
+\item check that all pLTS labels (action, guard, assignment) in
 the transition, the OT predicate, and the OT assignments are
@@
 predicate simplification is using `some form of ``tautology checking''
-rather than rewritting.}
+rather than rewriting.}
 
@@
     ot_1  = &\openrule{\{s0 \xrightarrow{\OTvar{fail(true)}} s1, t0 \xrightarrow{\OTvar{start(true)}} t1\}, ~~\{\xrightarrow{hb_1}\},~~\OTvar{fail(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
-    \OTland \OTvar{start(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland hb_1=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\OTland v_1=\OTvar{\underline{fail}}\OTland \OTvar{b}_1 = \OTvar{b}_2
+    \OTland \OTvar{start(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland hb_1=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\\
+    \OTland v_1=\OTvar{\underline{fail}}\OTland \OTvar{b}_1 = \OTvar{b}_2
     \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{t := Max\}}
@@
     ot_2  = &\openrule{\{s0 \xrightarrow{\OTvar{resume(false)}} s0, t0 \xrightarrow{\OTvar{resume(false)}} t0\}, ~~\{\xrightarrow{hb_2}\},~~\OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_1\OTvar{)}\\
-    \OTland \OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_2=\OTvar{resume(}\OTvar{b}_0\OTvar{)}\OTland v_2=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
+    \OTland \OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_2=\OTvar{resume(}\OTvar{b}_0\OTvar{)}\\
+    \OTland v_2=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
     \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
@@
     ot_4  = &\openrule{\{s1 \xrightarrow{\OTvar{fail(false)}} s1, t1 \xrightarrow{\OTvar{start(false)}} t1\}, ~~\{\xrightarrow{hb_4}\},~~\OTvar{fail(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
-    \OTland \OTvar{start(false)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland hb_4=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\OTland v_4=\OTvar{\underline{fail}}\OTland \OTvar{b}_1 = \OTvar{b}_2
+    \OTland \OTvar{start(false)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland hb_4=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\\
+    \OTland v_4=\OTvar{\underline{fail}}\OTland \OTvar{b}_1 = \OTvar{b}_2
     \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
@@
     ot_5  = &\openrule{\{s1 \xrightarrow{\OTvar{resume(true)}} s0, t1 \xrightarrow{\OTvar{resume(true)}} t0\}, ~~\{\xrightarrow{hb_5}\},~~\OTvar{resume(true)}=\OTvar{resume(}\OTvar{b}_1\OTvar{)}\\
-    \OTland \OTvar{resume(true)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_2=\OTvar{resume(}\OTvar{b}_0\OTvar{)}\OTland v_5=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
+    \OTland \OTvar{resume(true)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_2=\OTvar{resume(}\OTvar{b}_0\OTvar{)}\\
+    \OTland v_5=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
     \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
@@
     ot_9  = &\openrule{\{s2 \xrightarrow{\OTvar{resume(false)}} s2, t0 \xrightarrow{\OTvar{resume(false)}} t0\}, ~~\{\xrightarrow{hb_9}\},~~\OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_1\OTvar{)}\\
-    \OTland \OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_9=\OTvar{resume(}\OTvar{b}_0\OTvar{)}\OTland v_9=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
+    \OTland \OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_9=\OTvar{resume(}\OTvar{b}_0\OTvar{)}\\
+    \OTland v_9=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
     \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}

### 2018-01-19 2017-Xudong-SMT/FM-2018-extended.tex
reductions parties principales

@@
 \begin{table}\caption{\label{table:BIPalgebra}\leftline{Algebra
-      Presentation: predefined and BIP Sorts and Operators}}
+      Presentation: predefined Sorts and Operators}}
 	\begin{tabular}{p{3cm}p{3cm}p{6cm}}
@@
                 \\\specialrule{0em}{1pt}{1pt} 
-		Action 			&  $\texttt{Synchro},\ \texttt{FUN\_Action\_Bool}$ &
+                %               		Action 			&  $\texttt{Synchro},\ \texttt{FUN\_Action\_Bool}$ &
+                Action 			&  $\texttt{Synchro},\ \texttt{FUN}$ &
                 \\\specialrule{0em}{1pt}{1pt}
@@
 %                \textsl{for any sort} & & $=,\ \ne$
+		\\\hline\specialrule{0em}{1pt}{1pt}
+\multicolumn{3}{l}{\sl Extension for the BIP use-case of Fig.~\ref{schema:ArchFailure:pNet}}
+		\\\hline\specialrule{0em}{1pt}{1pt}
+                Action & \multicolumn{2}{l} \texttt{FUN\_Action\_Bool}, \texttt{}fail, resume, timeout, reset, start, tick, ask 
 		\\\hline
@@
 The semantics of pNet in term of open automata has been defined in
-\cite{henrio:Forte2016}. For convenience we include these 
-rules in appendix \ref{appendix:semRules}.
+\cite{henrio:Forte2016}, in the form of 2 structural rules, one for
+pLTSs, one for pNet nodes.. For convenience we include these rules in
+appendix \ref{appendix:semRules}.
 
@@
 Our algorithm starts with an open pNet, and builds its set of open
-transitions (OTs). Its main loop is a classical residual algorithm: starting
-from the initial global state, it pick a state in an unexplored set, and
+transitions. Its main loop is a classical residual algorithm: starting
+from the initial global state, it picks a state in an unexplored set, and
 computes all possible OTs, adding their target states in the
@@
 \Require The pNet node P.
-\State Initialize sets $U$, $E$ for unexplored/explored global states, $L$ for result OTs;
+\State Initialize sets $U=InitSate(P)$, $E=\emptyset$ for unexplored/explored global states, $L$ for result OTs;
 \While{!isEmpty(U)}
@@
 \State Prune the open transitions in $L$ using the SMT solver;
-\State \Return $L$;
+\State \Return $OA=Reachable(InitState(P),L)$;
 
@@
 the semantic rules following the structure of the pNet. 
-For pLTS at leaves, rule Tr1 simply take the pLTS transitions of the
+For pLTS at leaves, we simply take the pLTS transitions of the
 corresponding local state and build the predicate to generate the
 open transition. 
-On a pNet node to apply rule Tr2 we use two methods, combining and
-matching, to generate the new predicate of the open transitions in a
+On a pNet node we use two methods, combining and
+matching, to generate the predicate of the open transitions in a
 hierarchical manner.
 
-Last, at the root of the pNet, the predicate of each OT is translated
+Then, at the root of the pNet, the predicate of each OT is translated
 into SMTlib assertions, and checked for satisfiability. Unsatisfiable
@@
 \begin{algorithmic}[1]
-\Require The pNet node P; The start global state S.
+\Require a pNet node Pn; a global state S.
 \State Initialize a list $l$, $L$ for sub-transitions/transitions.
-	\For{each Subnet in P}
-	\\ ~~~ $\setminus \setminus$ Recursively applying Tr1 or Tr2 on the sub-nodes.
+	\For{each Subnet in Pn}
+	~~~ $\setminus \setminus$ Recursively applying Tr1 or Tr2 on the sub-nodes.
                 \State Store MakeTransitions(Subnet, S) in $l$;
@@
 	\For{each $sv \in SV$}
-		\State $comb = Combining(l)$;
-                 \State $ot = Matching(sv, comb, hole, v)$;
-                 \State Store $ot$ in $L$; 
+		\State $\overline{comb} = Combining(l)$;
+                 \State $ot = Matching(sv, \overline{comb}, hole, v)$;
+                 \State Store $ot$ in $L$; ~~~ $\setminus \setminus$ if Filter(ot) succeeds
 	\EndFor
@@
 subnets, as all the possible combinations of their open transitions.
-Assume that there is a collection of $n$ subnets $L = {s_1, s_2, ...,
-  s_n}$, if we notate $ot_i$ to be the set of open transitions of the
-subnet $s_i$ and ``$-$'' means the subnet is not involved.  
-Then the combination $\texttt{COMB}$, a set of n-tuples, is the
+Assume that there is a collection of $n$ subnets
+$L = {s_1, s_2, ...,  s_n}$; we denote $\overline{ot}_i$ the set of open
+transitions of the 
+subnet $s_i$ and ``$-$'' means the subnet is not involved;
+then the combination $\overline{comb}$, a set of n-tuples, is the
 cartesian product of sets :  
-$\texttt{COMB} : (\inactive\cup ot_1) \times (\inactive\cup ot_2)\times ... \times (\inactive\cup ot_n) .$
+$\overline{comb} : (\inactive\cup \overline{ot}_1) \times (\inactive\cup \overline{ot}_2)\times ... \times (\inactive\cup \overline{ot}_n).$
 
@@
 and its guard $G_k$, a tuple of open transitions
-$C_n\in \texttt{COMB} = {(v_i)}^{i\in I}$, the hole behaviors $Hole$,
+$C_n\in \overline{comb} = {(v_i)}^{i\in I}$, the hole behaviors $Hole$,
 and a fresh variable representing the result action $v$, we build the
@@
 
-Each of these possible failures is more precise than the previous
+Each of these possible filters is more precise than the previous
 ones. But even when unification succeeds, it is still possible that
@@
 that assign potentially different values to a state variable.
-To handle such cases, the algorithm manages the assignments
-within a list for each pLTS.
-The list we used contains triples <$v$, $S$, $AssignRH$> 
-where $v$ is the variable in pLTS, $S$ is its owner state and
-$AssignRH$ is a list of expressions over other variables in the right
-hand side of assignments of $v$.
+To handle such cases, the algorithm manages for each pLTS state, as a
+list of expressions collected from the assignments of each state
+variable $v$.
+%% The list we used contains triples <$v$, $S$, $AssignRH$> 
+%% where $v$ is the variable in pLTS, $S$ is its owner state and
+%% $AssignRH$ is a list of expressions over other variables in the right
+%% hand side of assignments of $v$.
 % As a pragmatic extension to the formal definition, we also manage
@@
 of state variables of the individual pLTS states constituting this
-global state (variables of different pLTS are distinct). We define:
-\begin{itemize}
-  \item $SVars(gs)$ the state variables of all states in the global
-    state $gs$
-  \item $Assigns(svar)$ the set of possible assignments of variable
-      $svar$.
-\end{itemize}
-
+global state (variables of different pLTS are distinct).
 %There are some assignment on the variables in each of states of the pLTS (state variables), or just as global states of it (global variables).
@@
 executes a ``$resume$''. The chosen synchronization
-vector (SV0) does not match with these actions, as shown the predicate
+vector (SV0 from Fig.~\ref{schema:ArchFailure:pNet}) does not match
+with these actions, as shown by the predicate
 fragment ``resume(true)=start($b_2$)''.
@@
   \end{mathpar}
-\caption{One of the unsatisfiable open transitions in FailureTimer}  \label{schema:unsat-ot}
+\caption{One of the unsatisfiable open transitions in the Failure Monitor pNet}  \label{schema:unsat-ot}
 \end{figure}
@@
 on the action expressions and the predicates, and this 
-may depend on the specific theory of the action algebra. 
+may depend on the specific theory of the action algebra datatypes. 
 The ``Modulo Theory'' part of SMT solvers is important here, so that
@@
 
-As the last step of \ref{alg1}, we use the SMT solver Z3 to check the
-satisfiability of each open transitions. More precisely, we translate
+We check the satisfiability of each open transitions
+using the SMT solver Z3. More precisely, we translate
 the OT predicate into a SMTlib assertion, in the context provided by
@@
 refinements.
-
-Before that work, we need to reconsider the result open transitions
-from our algorithm. The ideal
-result that we showed in the bottom part of
-Fig.~\ref{schema:resultOA} is not the one generated by the algorithm,
-because the original one contains many intermediate
-variables, such as fresh local variables of synchronization
-vectors, and fresh result variables of intermediate open transitions.
-Such intermediate variables come from the way predicates are
-generated, and depends on the particular structure of the pNet. But
-they are not significant in the resulting behavior, and should be
-eliminated before comparing such behavior with another pNet.
-To eliminate the intermediate variables in the predicate, we want to define
-the set of the significant variables that we won't eliminate: the
-local variables of pLTS transitions, the hole behaviors and the result
-action at the top level.
-The result of the elimination will be simpler predicates, that can be
-successfully compared (e.g. by Z3) within the bisimulation checking
-algorithm.
 
@@
 
+In rule TR2, the generated predicate is composed of the conjunction of
+the predicates of the subnets' OTs, with the additional part encoding
+the application of the chosen synchronisation vector.
+In \cite{henrio:Forte2016} this last part is defined as:
+\[\MkPred(SV_k, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow
+\begin{array}{l}
+\exists {(a'_i)}^{i\in I},
+{(b'_j)}^{j\in J},v'.\, SV_k={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v'
+\\~~\land
+\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v'
+\end{array}\]
+
+This definition is not constructive, but the existentialy quantified
+variable sets here correspond the subsets of subnets and holes that
+are effectively involved in vector $SV_k$.
+Within our algorithm, these subsets have been computed by $Combining$ and
+passed as arguments to the $Matching$ method, so
+we can construct this predicate fragment as:
+
+\[\Pred(SV, \overline{\pNet},\overline{S}, v) = 
+\begin{array}{l}
+\forall {(a'_i)}^{i\in I},
+{(b'_j)}^{j\in J},v'.
+\\
+v_m=a'_i\land \, b_j=b'_j \land v=v' \land G_k
+\end{array}\]
+\TODO{Eric: to be checked}
+
 \begin{theorem}[Finiteness of open-automata.]\\
@@
    \item[$\bullet$] $prefix$ identifies the kind of the
-     variable. current kinds are: sva (SV action), ra (result action), hb (hole behavior).
-   \item[$\bullet$] $tree\ index$ is the index of the node containing the variable in the tree-like structure of the pNet.
+     variable. Current kinds are: sva\_<SV> (action variable in vector
+     $SV$), ra (result action), hb\_<B> (behavior of hole $B$).
+   \item[$\bullet$] $tree\ index$ is the index of the node containing
+     the variable in the tree-like structure of the pNet. 
    \item[$\bullet$] $counter$ is the current value of the corresponding counter.
@@
 
-For example, in the running example, the first possible behavior of
-the hole, it doesn't have a name, only have the prefix ``hb''. The
-hole is the second subnets of the root node so its ``tree index'' is
-``12''. The fresh variable name is ``$\OTvar{:hb:12:1}$''.
+For example, in the running example, in the raw output listing in
+Appendix~ref{}, in the first OT, you find variables: 
+\begin{itemize}
+   \item $\OTvar{:hb\_B:13:1}$ that is the behaviour of hole ``B''
+   \item $\OTvar{b1:sva\_SV0:1:1}$ variable ``b1'' from vector ``SV0''
+   \item $\OTvar{:ra:1:1}$ result action of the current OT
+\end{itemize}
 
@@
 
+\section{Management of state variables}
+\label{appendix:translating-assignments}
+In a pLTS, there may be several incoming transitions 
+that assign potentially different values to a state variable.
+To handle such cases, the algorithm manages for each pLTS state, as a
+list of expressions collected from the assignments of each state
+variable $v$ (as registered in the incoming OTs).
+%% The list we used contains triples <$v$, $S$, $AssignRH$> 
+%% where $v$ is the variable in pLTS, $S$ is its owner state and
+%% $AssignRH$ is a list of expressions over other variables in the right
+%% hand side of assignments of $v$.
+% As a pragmatic extension to the formal definition, we also manage
+% ``global variables'', defined in all states of the pLTS.
+For a global state in the open automaton, getting the set of state
+variables (which may be used in a transition) will simply be the union
+of state variables of the individual pLTS states constituting this
+global state, as variables of different pLTS are distinct.
+
+ We define:
+\begin{itemize}
+  \item $SVars(gs)$ the state variables of all states in the global
+    state $gs$
+  \item $Assigns(svar)$ the set of possible assignments of variable
+      $svar$.
+\end{itemize}
+These will be used when translating the predicates into SMTlib
+language.
+
 \section{Translation to SMTlib input language}
@@
 The pNet elements, as defined above, can be full translated into
-SMT-LIB language, but there are a number of differences in the
+SMT-LIB language (\ref{SMTlibv2.5}), but there are a number of differences in the
 structure of the models/languages, so the translation is not trivial.
@@
 
-\QIN{Each time we submit each open transition to Z3 module, we translate
-  its predicate into Z3 language format and send it for satisfiability
+Each time we submit each open transition to Z3 module, we translate
+  its predicate into the SMTlib language  and send it for satisfiability
   checking. Every term of the predicate is declared as an
@@
   declare them before the submission of a predicate term with the API
-  method conducting \texttt{declare-const}.}
+  method conducting \texttt{declare-const}.
 
@@
   get the state variables and their possible evaluations from all the state in $gs$.
-  Then use Ass(x) as the set of evaluations of state variable x.
+  Then use Assigns(x) as the set of evaluations of state variable x.
 \item for each variable $v$ in $\EEnv$, construct:
@@
 
-\paragraph{Translating assignments into predicate terms}
-\label{appendix:translating-assignments}
-\TODO{INCORRECT, to be rewritten}
-State-variable assignments are also treated as a part of the
-predicates when checking the satisfiability. % Here we need conduct some
-% translations,
-For each assignement in a $\Post$ predicate, such as $\{s_0 \leftarrow 1\}$ in section
-~\ref{section:op-semantics}, we translate it into an equation
-$s_0=1$. For several assignments of the same variable in the same state,
-we generate the disjunction of 
-these equations. Correspondingly, we generate a conjunction for the
-assignments from different variables.
-
-%% \paragraph{Checking satisfiability}
-
-%% % We check the satisfiability of open transitions on the top level of
-%% % the pNet, treating these open transitions as the intermediate result
-%% % of the algorithm. After we get the intermediate results of open
-%% % transitions, we check them one by one.
-%% Here we declare first all the variables in the predicates, with their
-%% sorts.
-%% An example of syntax is::\\
-%% \centerline{$\OTvar{(declare-const\ |:ra:1:1|\ Action)}$}
-
-%% \noindent Then each term of the
-%% predicate is an assertion in Z3, as an example, in the former
-%% unsatisfiable result in Fig~\ref{schema:unsat-ot}, the contradiction is occurred in terms: \\
-%% \centerline{$\OTvar{(:ra:11:1=l)} \OTland \OTvar{(delta=:ra:11:1)}$}\\
-%% from which we generate the following two assertions:\\
-%% \centerline{$\OTvar{(assert\ (=\ |:ra:11:1|\ l))\ \ \ (assert\ (=\ delta\ |:ra:11:1|))}$}
-
-%% \noindent The predicate submitted to the Z3 also contains the
-%% assignments encodings.
-%% In the case of $ot_2$, it
-%% gives the assertion:\\
-%% \centerline{$\OTvar{assert (or (= var\_s0 0) (= var\_s0 01)))}$}
+\subsection{properties}
+The rules in the sections above are meant to guarantee that no runtime
+errors would occur when running Z3 from our algorithm. More precisely,
+we ensure that:
+\begin{itemize}
+\item all datatypes, functions, variable used are declared,
+\item datatypes declared are well-founded,
+\item all expressions in declarations and assertions are well-typed.
+\end{itemize}
+
+\section{Full output for the FailureTimer open automaton}
+\label{appendix:fullOutput}
+
+\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, frame=single]
+	{s0---failure(true)-->s1, t0---start(true)-->t1},{---:hb_B:13:1-->},   
+	(failure(true)=failure(b1:sva_SV0:1:1))
+	/\(start(true)=start(b2:sva_SV0:1:1))
+	/\(:hb_B:13:1=fail(b0:sva_SV0:1:1))/\((b1:sva_SV0:1:1=b2:sva_SV0:1:1)
+	/\(~(b1:sva_SV0:1:1\/b2:sva_SV0:1:1)\/b0:sva_SV0:1:1))
+	/\(_fail_=:ra:1:1),{t := Max}
+OT ---------------------------------------------------------------------------
+		<s0_t0>-----:ra:1:1----><s1_t1>
+
+	{s0---resume(false)-->s0, t0---resume(false)-->t0},{---:hb_B:16:2-->},   
+	(resume(false)=resume(b1:sva_SV1:1:2))
+	/\(resume(false)=resume(b2:sva_SV1:1:2))
+	/\(:hb_B:16:2=resume(b0:sva_SV1:1:2))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2)
+	/\(~(b1:sva_SV1:1:2\/b2:sva_SV1:1:2)\/b0:sva_SV1:1:2)
+	/\(_resume_=:ra:1:2),{}
+OT ---------------------------------------------------------------------------
+	<s0_t0>-----:ra:1:2----><s0_t0>
+
+	{},{---:hb_B:118:6-->},(:hb_B:118:6=finish)/\(finish=:ra:1:6),{}
+OT ---------------------------------------------------------------------------
+	<s0_t0>-----:ra:1:6----><s0_t0>
+
+	{s1---failure(false)-->s1, t1---start(false)-->t1},{---:hb_B:13:1-->},   
+	(failure(false)=failure(b1:sva_SV0:1:1))
+	/\(start(false)=start(b2:sva_SV0:1:1))
+	/\(:hb_B:13:1=fail(b0:sva_SV0:1:1))/\((b1:sva_SV0:1:1=b2:sva_SV0:1:1)
+	/\(~(b1:sva_SV0:1:1\/b2:sva_SV0:1:1)\/b0:sva_SV0:1:1))
+	/\(_fail_=:ra:1:1),{}
+OT ---------------------------------------------------------------------------
+	<s1_t1>-----:ra:1:1----><s1_t1>
+
+	{s1---resume(true)-->s0, t1---resume(true)-->t0},{---:hb_B:16:2-->},   
+	(resume(true)=resume(b1:sva_SV1:1:2))
+	/\(resume(true)=resume(b2:sva_SV1:1:2))
+	/\(:hb_B:16:2=resume(b0:sva_SV1:1:2))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2)
+	/\(~(b1:sva_SV1:1:2\/b2:sva_SV1:1:2)\/b0:sva_SV1:1:2))
+	/\(_resume_=:ra:1:2),{}
+OT ---------------------------------------------------------------------------
+	<s1_t1>-----:ra:1:2----><s0_t0>
+
+	{t1---tick-->t1},{},(t>0)/\(tick=:ra:1:3),{t := (t-1)}
+OT ---------------------------------------------------------------------------
+	<s1_t1>-----:ra:1:3----><s1_t1>
+
+	{},{---:hb_B:118:6-->},(:hb_B:118:6=finish)/\(finish=:ra:1:6),{}
+OT ---------------------------------------------------------------------------
+	<s1_t1>-----:ra:1:6----><s1_t1>
+
+	{s1---timeout-->s2, t1---timeout-->t0}, {},(t=0)/\(ask=:ra:1:4),{}
+OT ---------------------------------------------------------------------------
+	<s1_t1>-----:ra:1:4----><s2_t0>
+
+	{s2---resume(false)-->s2, t0---resume(false)-->t0},{---:hb_B:16:2-->},   
+	(resume(false)=resume(b1:sva_SV1:1:2))
+	/\(resume(false)=resume(b2:sva_SV1:1:2))
+	/\(:hb_B:16:2=resume(b0:sva_SV1:1:2))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2)
+	/\(~(b1:sva_SV1:1:2\/b2:sva_SV1:1:2)\/b0:sva_SV1:1:2))
+	/\(_resume_=:ra:1:2),{}
+OT ---------------------------------------------------------------------------
+	<s2_t0>-----:ra:1:2----><s2_t0>
+
+	{s2---reset-->s0},{},(reset=:ra:1:5),{}
+OT ---------------------------------------------------------------------------
+	<s2_t0>-----:ra:1:5----><s0_t0>
+
+	{},{---:hb_B:118:6-->},(:hb_B:118:6=finish)/\(finish=:ra:1:6),{}
+OT ---------------------------------------------------------------------------
+	<s2_t0>-----:ra:1:6----><s2_t0>
+\end{lstlisting}
+
+\newpage
+\begin{figure}[h]
+$\begin{array}{r@{}l}
+    ot_1  = &\openrule{\{s0 \xrightarrow{\OTvar{fail(true)}} s1, t0 \xrightarrow{\OTvar{start(true)}} t1\}, ~~\{\xrightarrow{hb_1}\},~~\OTvar{fail(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
+    \OTland \OTvar{start(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland hb_1=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\\
+    \OTland v_1=\OTvar{\underline{fail}}\OTland \OTvar{b}_1 = \OTvar{b}_2
+    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{t := Max\}}
+    	   {\ostate{s0,t0} \xrightarrow{v_1} \ostate{s1,t1}}\\
+\end{array}$
+  \smallskip
+
+$\begin{array}{r@{}l}
+    ot_2  = &\openrule{\{s0 \xrightarrow{\OTvar{resume(false)}} s0, t0 \xrightarrow{\OTvar{resume(false)}} t0\}, ~~\{\xrightarrow{hb_2}\},~~\OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_1\OTvar{)}\\
+    \OTland \OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_2=\OTvar{resume(}\OTvar{b}_0\OTvar{)}\\
+    \OTland v_2=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
+    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
+    	    {\ostate{s0,t0} \xrightarrow{v_2} \ostate{s0,t0}}\\
+  \end{array}$
+\smallskip
+
+$\begin{array}{r@{}l}
+    ot_3  = &\openrule{\{\}, ~~\{\xrightarrow{hb_3}\},~~hb_3=\OTvar{finish}\OTland v_3=\OTvar{finish}, ~~\{\}}
+    	    {\ostate{s0,t0} \xrightarrow{v_3} \ostate{s0,t0}}\\
+\end{array}$
+\smallskip
+
+$\begin{array}{r@{}l}
+    ot_4  = &\openrule{\{s1 \xrightarrow{\OTvar{fail(false)}} s1, t1 \xrightarrow{\OTvar{start(false)}} t1\}, ~~\{\xrightarrow{hb_4}\},~~\OTvar{fail(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
+    \OTland \OTvar{start(false)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland hb_4=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\\
+    \OTland v_4=\OTvar{\underline{fail}}\OTland \OTvar{b}_1 = \OTvar{b}_2
+    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
+    	   {\ostate{s1,t1} \xrightarrow{v_4} \ostate{s1,t1}}\\
+\end{array}$
+\smallskip
+
+$\begin{array}{r@{}l}
+    ot_5  = &\openrule{\{s1 \xrightarrow{\OTvar{resume(true)}} s0, t1 \xrightarrow{\OTvar{resume(true)}} t0\}, ~~\{\xrightarrow{hb_5}\},~~\OTvar{resume(true)}=\OTvar{resume(}\OTvar{b}_1\OTvar{)}\\
+    \OTland \OTvar{resume(true)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_2=\OTvar{resume(}\OTvar{b}_0\OTvar{)}\\
+    \OTland v_5=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
+    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
+    	    {\ostate{s1,t1} \xrightarrow{v_5} \ostate{s0,t0}}\\
+\end{array}$
+\smallskip
+
+$\begin{array}{r@{}l}
+    ot_6  = &\openrule{\{t1 \xrightarrow{\OTvar{tick}} t1\}, ~~\{\},~~t\neq 0\OTland v_6=\OTvar{tick}, ~~\{t := t-1 \}}
+    	   {\ostate{s1,t1} \xrightarrow{v_6} \ostate{s1,t0}}\\
+\end{array}$
+\smallskip
+
+$\begin{array}{r@{}l}
+    ot_7  = &\openrule{\{\}, ~~\{\xrightarrow{hb_7}\},~~hb_7=\OTvar{finish}\OTland v_7=\OTvar{finish}, ~~\{\}}
+    	    {\ostate{s1,t1} \xrightarrow{v_7} \ostate{s1,t1}}\\
+\end{array}$
+\smallskip
+
+$\begin{array}{r@{}l}
+    ot_8  = &\openrule{\{s1 \xrightarrow{\OTvar{timeout}} s2, t1 \xrightarrow{\OTvar{timeout}} t0\}, ~~\{\},~~t=0\OTland v_8=ask, ~~\{\}}
+    	   {\ostate{s1,t1} \xrightarrow{v_8} \ostate{s2,t0}}\\
+\end{array}$
+\smallskip
+
+$\begin{array}{r@{}l}
+    ot_9  = &\openrule{\{s2 \xrightarrow{\OTvar{resume(false)}} s2, t0 \xrightarrow{\OTvar{resume(false)}} t0\}, ~~\{\xrightarrow{hb_9}\},~~\OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_1\OTvar{)}\\
+    \OTland \OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_9=\OTvar{resume(}\OTvar{b}_0\OTvar{)}\\
+    \OTland v_9=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
+    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
+    	    {\ostate{s2,t0} \xrightarrow{v_9} \ostate{s2,t0}}\\
+\end{array}$
+\smallskip
+
+$\begin{array}{r@{}l}
+    ot_{10}  = &\openrule{\{s2 \xrightarrow{\OTvar{reset}} s0\}, ~~\{\},~~v_{10}=\OTvar{reset}, ~~\{\}}
+    	   {\ostate{s2,t0} \xrightarrow{v_{10}} \ostate{s0,t0}}\\
+\end{array}$
+\smallskip
+
+$\begin{array}{r@{}l}
+    ot_{11}  = &\openrule{\{\}, ~~\{hb_{11}\},~~hb_{11}=\OTvar{finish}\OTland v_{11}=\OTvar{finish}, ~~\{\}}
+    	   {\ostate{s2,t0} \xrightarrow{v_{11}} \ostate{s2,t0}}\\
+\end{array}$
+\caption{The open transitions of the open automaton}  \label{schema:ots}
+\end{figure}
+
+\newpage
+\subsection{Scaling up: several subsystems on the same bus}
+
+\TODO{Not yet !}
+
+\end{document}
 
@@
 }
-
-\section{Full output for the FailureTimer open automaton}
-\label{appendix:fullOutput}
-
-\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, frame=single]
-	{s0---failure(true)-->s1, t0---start(true)-->t1},{---:hb_B:13:1-->},   
-	(failure(true)=failure(b1:sva_SV0:1:1))
-	/\(start(true)=start(b2:sva_SV0:1:1))
-	/\(:hb_B:13:1=fail(b0:sva_SV0:1:1))/\((b1:sva_SV0:1:1=b2:sva_SV0:1:1)
-	/\(~(b1:sva_SV0:1:1\/b2:sva_SV0:1:1)\/b0:sva_SV0:1:1))
-	/\(_fail_=:ra:1:1),{t := Max}
-OT ---------------------------------------------------------------------------
-		<s0_t0>-----:ra:1:1----><s1_t1>
-
-	{s0---resume(false)-->s0, t0---resume(false)-->t0},{---:hb_B:16:2-->},   
-	(resume(false)=resume(b1:sva_SV1:1:2))
-	/\(resume(false)=resume(b2:sva_SV1:1:2))
-	/\(:hb_B:16:2=resume(b0:sva_SV1:1:2))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2)
-	/\(~(b1:sva_SV1:1:2\/b2:sva_SV1:1:2)\/b0:sva_SV1:1:2)
-	/\(_resume_=:ra:1:2),{}
-OT ---------------------------------------------------------------------------
-	<s0_t0>-----:ra:1:2----><s0_t0>
-
-	{},{---:hb_B:118:6-->},(:hb_B:118:6=finish)/\(finish=:ra:1:6),{}
-OT ---------------------------------------------------------------------------
-	<s0_t0>-----:ra:1:6----><s0_t0>
-
-	{s1---failure(false)-->s1, t1---start(false)-->t1},{---:hb_B:13:1-->},   
-	(failure(false)=failure(b1:sva_SV0:1:1))
-	/\(start(false)=start(b2:sva_SV0:1:1))
-	/\(:hb_B:13:1=fail(b0:sva_SV0:1:1))/\((b1:sva_SV0:1:1=b2:sva_SV0:1:1)
-	/\(~(b1:sva_SV0:1:1\/b2:sva_SV0:1:1)\/b0:sva_SV0:1:1))
-	/\(_fail_=:ra:1:1),{}
-OT ---------------------------------------------------------------------------
-	<s1_t1>-----:ra:1:1----><s1_t1>
-
-	{s1---resume(true)-->s0, t1---resume(true)-->t0},{---:hb_B:16:2-->},   
-	(resume(true)=resume(b1:sva_SV1:1:2))
-	/\(resume(true)=resume(b2:sva_SV1:1:2))
-	/\(:hb_B:16:2=resume(b0:sva_SV1:1:2))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2)
-	/\(~(b1:sva_SV1:1:2\/b2:sva_SV1:1:2)\/b0:sva_SV1:1:2))
-	/\(_resume_=:ra:1:2),{}
-OT ---------------------------------------------------------------------------
-	<s1_t1>-----:ra:1:2----><s0_t0>
-
-	{t1---tick-->t1},{},(t>0)/\(tick=:ra:1:3),{t := (t-1)}
-OT ---------------------------------------------------------------------------
-	<s1_t1>-----:ra:1:3----><s1_t1>
-
-	{},{---:hb_B:118:6-->},(:hb_B:118:6=finish)/\(finish=:ra:1:6),{}
-OT ---------------------------------------------------------------------------
-	<s1_t1>-----:ra:1:6----><s1_t1>
-
-	{s1---timeout-->s2, t1---timeout-->t0}, {},(t=0)/\(ask=:ra:1:4),{}
-OT ---------------------------------------------------------------------------
-	<s1_t1>-----:ra:1:4----><s2_t0>
-
-	{s2---resume(false)-->s2, t0---resume(false)-->t0},{---:hb_B:16:2-->},   
-	(resume(false)=resume(b1:sva_SV1:1:2))
-	/\(resume(false)=resume(b2:sva_SV1:1:2))
-	/\(:hb_B:16:2=resume(b0:sva_SV1:1:2))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2)
-	/\(~(b1:sva_SV1:1:2\/b2:sva_SV1:1:2)\/b0:sva_SV1:1:2))
-	/\(_resume_=:ra:1:2),{}
-OT ---------------------------------------------------------------------------
-	<s2_t0>-----:ra:1:2----><s2_t0>
-
-	{s2---reset-->s0},{},(reset=:ra:1:5),{}
-OT ---------------------------------------------------------------------------
-	<s2_t0>-----:ra:1:5----><s0_t0>
-
-	{},{---:hb_B:118:6-->},(:hb_B:118:6=finish)/\(finish=:ra:1:6),{}
-OT ---------------------------------------------------------------------------
-	<s2_t0>-----:ra:1:6----><s2_t0>
-\end{lstlisting}
-
-\begin{figure}[h]  
-$\begin{array}{r@{}l}
-    ot_1  = &\openrule{\{s0 \xrightarrow{\OTvar{fail(true)}} s1, t0 \xrightarrow{\OTvar{start(true)}} t1\}, ~~\{\xrightarrow{hb_1}\},~~\OTvar{fail(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
-    \OTland \OTvar{start(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland hb_1=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\\
-    \OTland v_1=\OTvar{\underline{fail}}\OTland \OTvar{b}_1 = \OTvar{b}_2
-    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{t := Max\}}
-    	   {\ostate{s0,t0} \xrightarrow{v_1} \ostate{s1,t1}}\\
-\end{array}$
-
-$\begin{array}{r@{}l}
-    ot_2  = &\openrule{\{s0 \xrightarrow{\OTvar{resume(false)}} s0, t0 \xrightarrow{\OTvar{resume(false)}} t0\}, ~~\{\xrightarrow{hb_2}\},~~\OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_1\OTvar{)}\\
-    \OTland \OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_2=\OTvar{resume(}\OTvar{b}_0\OTvar{)}\\
-    \OTland v_2=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
-    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
-    	    {\ostate{s0,t0} \xrightarrow{v_2} \ostate{s0,t0}}\\
-\end{array}$
-
-$\begin{array}{r@{}l}
-    ot_3  = &\openrule{\{\}, ~~\{\xrightarrow{hb_3}\},~~hb_3=\OTvar{finish}\OTland v_3=\OTvar{finish}, ~~\{\}}
-    	    {\ostate{s0,t0} \xrightarrow{v_3} \ostate{s0,t0}}\\
-\end{array}$
-
-$\begin{array}{r@{}l}
-    ot_4  = &\openrule{\{s1 \xrightarrow{\OTvar{fail(false)}} s1, t1 \xrightarrow{\OTvar{start(false)}} t1\}, ~~\{\xrightarrow{hb_4}\},~~\OTvar{fail(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
-    \OTland \OTvar{start(false)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland hb_4=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\\
-    \OTland v_4=\OTvar{\underline{fail}}\OTland \OTvar{b}_1 = \OTvar{b}_2
-    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
-    	   {\ostate{s1,t1} \xrightarrow{v_4} \ostate{s1,t1}}\\
-\end{array}$
-
-$\begin{array}{r@{}l}
-    ot_5  = &\openrule{\{s1 \xrightarrow{\OTvar{resume(true)}} s0, t1 \xrightarrow{\OTvar{resume(true)}} t0\}, ~~\{\xrightarrow{hb_5}\},~~\OTvar{resume(true)}=\OTvar{resume(}\OTvar{b}_1\OTvar{)}\\
-    \OTland \OTvar{resume(true)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_2=\OTvar{resume(}\OTvar{b}_0\OTvar{)}\\
-    \OTland v_5=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
-    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
-    	    {\ostate{s1,t1} \xrightarrow{v_5} \ostate{s0,t0}}\\
-\end{array}$
-
-$\begin{array}{r@{}l}
-    ot_6  = &\openrule{\{t1 \xrightarrow{\OTvar{tick}} t1\}, ~~\{\},~~t\neq 0\OTland v_6=\OTvar{tick}, ~~\{t := t-1 \}}
-    	   {\ostate{s1,t1} \xrightarrow{v_6} \ostate{s1,t0}}\\
-\end{array}$
-
-$\begin{array}{r@{}l}
-    ot_7  = &\openrule{\{\}, ~~\{\xrightarrow{hb_7}\},~~hb_7=\OTvar{finish}\OTland v_7=\OTvar{finish}, ~~\{\}}
-    	    {\ostate{s1,t1} \xrightarrow{v_7} \ostate{s1,t1}}\\
-\end{array}$
-
-$\begin{array}{r@{}l}
-    ot_8  = &\openrule{\{s1 \xrightarrow{\OTvar{timeout}} s2, t1 \xrightarrow{\OTvar{timeout}} t0\}, ~~\{\},~~t=0\OTland v_8=ask, ~~\{\}}
-    	   {\ostate{s1,t1} \xrightarrow{v_8} \ostate{s2,t0}}\\
-\end{array}$
-
-$\begin{array}{r@{}l}
-    ot_9  = &\openrule{\{s2 \xrightarrow{\OTvar{resume(false)}} s2, t0 \xrightarrow{\OTvar{resume(false)}} t0\}, ~~\{\xrightarrow{hb_9}\},~~\OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_1\OTvar{)}\\
-    \OTland \OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_9=\OTvar{resume(}\OTvar{b}_0\OTvar{)}\\
-    \OTland v_9=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
-    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
-    	    {\ostate{s2,t0} \xrightarrow{v_9} \ostate{s2,t0}}\\
-\end{array}$
-
-$\begin{array}{r@{}l}
-    ot_{10}  = &\openrule{\{s2 \xrightarrow{\OTvar{reset}} s0\}, ~~\{\},~~v_{10}=\OTvar{reset}, ~~\{\}}
-    	   {\ostate{s2,t0} \xrightarrow{v_{10}} \ostate{s0,t0}}\\
-\end{array}$
-
-$\begin{array}{r@{}l}
-    ot_{11}  = &\openrule{\{\}, ~~\{hb_{11}\},~~hb_{11}=\OTvar{finish}\OTland v_{11}=\OTvar{finish}, ~~\{\}}
-    	   {\ostate{s2,t0} \xrightarrow{v_{11}} \ostate{s2,t0}}\\
-\end{array}$
-\caption{The open transitions of the open automaton}  \label{schema:ots}
-\end{figure}
-
-\subsection{Scaling up: several subsystems on the same bus}
-
-\TODO{Not yet !}
-
-\end{document}

### 2018-01-19 2017-Xudong-SMT/FM-2018-extended.tex
Added justification of properties in Section 5.4; Proof-reading, reduction and notes in other sections.

@@
 
-\paragraph{Related works}
+\paragraph{Related work.}
 
@@
 
-There is not much research work towards trying to develop symbolic bisimulation approaches
-for the value-passing process algebra and languages, as our long-term goals,
-especially no algorithm treatment of the symbolic systems developed by
+%% There is not much research work towards trying 
+Very few attempts were made to develop symbolic bisimulation approaches
+for the value-passing process algebras and languages\mdash our long-term goals\mdash
+especially, there is no algorithmic treatment of the symbolic systems developed by
 interacting with automatic theorem provers. The closest work is the
@@
 \paragraph*{Term algebra.}
-Our models rely on a notion of parameterized actions, that are
+Our models rely on a notion of parameterized actions that are
 symbolic expressions using data types and variables. As we want to encode
@@
 and $\P$ a set of variables. Within $\Talg$, we distinguish a set of
-data expressions $\mathcal{E}_\P$, including a set of boolean
+data expressions $\mathcal{E}_\P$, including a set of Boolean
 expressions $\mathcal{B}_{\P}$ ($\mathcal{B}_{\P}\subseteq\mathcal{E}_\P$).
@@
 
-pNets can encode naturally the notion of input actions as found
-e.g. in value-passing CCS 
+pNets can encode naturally the notion of input actions as found,
+\eg in value-passing CCS 
 \cite{Milner89} or of usual point-to-point message passing calculi,
 but it also allows 
-for more general mechanisms, like gate negotiation in Lotos, or broadcast
+for more general mechanisms, like gate negotiation in Lotos~\hl{\cite{lotos}}, or broadcast
 communications.
@@
 presentation''. It will be used to check the
-well-formness of a pNet system, and to define the translation of the pNet
+well-formedness of a pNet system, and to define the translation of the pNet
 semantics into the SMT engine input language.
@@
 \begin{definition}
-  An Algebra Presentation is a pair $\mathcal{P}=<Sorts,Constrs,Ops>$ where:
+  An \emph{algebra presentation} is a triple $\mathcal{P}=\langle\mathit{Sorts},\mathit{Constrs},\mathit{Ops}\rangle$, where
 
   \begin{itemize}
-  \item $Sorts$ is a set of Sort names
-    \footnote{Later we may want to extend this with Sort constructors,
-      like Array or Pair, but this is not needed now}
-  \item $Constrs$ is a set of constructor operators, with $Con$ the
-    constructor name, and arity: $arity(Con)=n \in \mathbb{N}$,
-    and with their signature and their associated selectors,
-    of the form: '$Con : (sel_1,sort_1), ... , (sel_n,sort_n) -> sort$'.
-    For each argument, the pair $(sel_i,sort_i)$ defines an auxiliary
-    operator of name $sel_i$ with signature $sel_i : sort -> sort_i$.
-    \item $Ops$ is a set of other (auxiliary) operators, with their
-      arity and signature, of the form: $Op : sort_1, ...  sort_n ->
-      sort$
-      \item $Constrs(sortname), Sels(sortname)$, respectively define the set of
-        constructors and selectors of sort $sortname$
+  \item $Sorts$ is a set of \emph{sorts}\noteSB{Commented out a footnote here\mdash check if still necessary.}
+    %% \footnote{Later we may want to extend this with Sort constructors,
+    %%   like Array or Pair, but this is not needed now}
+  \item $\mathit{Constrs}$ is a set of \emph{constructor operators}: for each $\mathit{Con} \in \mathit{Constrs}$, $arity(Con)=n \in \mathbb{N}$ is its arity 
+    and '$Con : (\mathit{sel}_1,\mathit{sort}_1), \dots, (\mathit{sel}_n,\mathit{sort}_n) \rightarrow \mathit{sort}$' is its signature with the associated selectors.
+    For each argument, the pair $(\mathit{sel}_i,\mathit{sort}_i)$ defines an auxiliary
+    operator of name $\mathit{sel}_i$ with signature $\mathit{sel}_i : \mathit{sort} \rightarrow \mathit{sort}_i$.
+    \item $Ops$ is a set of \emph{auxiliary operators}, with their
+      arity and signature, of the form: $Op : \mathit{sort}_1, \dots,  \mathit{sort}_n \rightarrow
+      \mathit{sort}$
+      \item $\mathit{Constrs}(\mathit{sortname})$ and $\mathit{Sels}(\mathit{sortname})$ are, respectively, the sets of
+        constructors and selectors of the sort $\mathit{sortname}$
   \end{itemize}
-  All sorts and operator names must be distinct.\\
-  Amongst Constructors, those of arity 0 are called constants, and we
-  define $Consts(\mathcal{P}) = \{Con \in Constrs. arity(Con)=0\}$.
+  \noteSB{I think this can be removed}\hl{All sorts and operator names must be distinct.}
+  Among constructors, those of arity 0 are called \emph{constants}:
+  $\mathit{Consts}(\mathcal{P}) = \{\mathit{Con} \in \mathit{Constrs}\,|\, \mathit{arity}(\mathit{Con})=0\}$.
 \end{definition}
@@
 overloaded \texttt{FUN} constructor, used to build actions with
-arguments, that will be instanciated to the required sorts for a given
+arguments, that will be instantiated to the required sorts for a given
 pNet.
 
-\begin{table}\caption{\label{table:BIPalgebra}\leftline{Algebra
+\begin{table}[t]\caption{\label{table:BIPalgebra}\leftline{Algebra
       Presentation: predefined Sorts and Operators}}
@@
 		\hline\specialrule{0em}{1pt}{1pt}
-		Sort & Constructors & Other Operators
+		Sort & Constructors & Auxiliary Operators
                 \\\specialrule{0em}{1pt}{1pt}
@@
                 $- \texttt{(unary)},\ +,\ -
-                \texttt{(binary)},\ \times,\ \div, \texttt{etc.}$
+                \texttt{(binary)},\ \times,\ \div \text{ \etc}$
 %                \\\specialrule{0em}{1pt}{1pt}
@@
 
-A pLTS is a labelled transition system with variables; variables can be
+A pLTS is a labelled transition system with variables, which can be
 manipulated, defined, or accessed inside states, actions, guards, and
 assignments. 
-
+%
 %Without loss of generality and to simplify the formalization, we suppose 
@@
 %variable values from one state to the other can be done by explicit assignment. 
-
-Each state has its set of variables called $State\ variables$, 
-which can only be modified by the assignment in the transitions targeting its owner state. 
+%
+Each state has its set of variables called \emph{state variables}, 
+which can only be modified by the assignment in transitions targeting this state. 
 A global state variable of a pLTS is a variable $x$ satisfying $\forall s\!\in\! S .\, x\!\in\! \vars(s)$.
-
+%
 %Similarly, to simplify the management of variables and without loss of expressivity, we 
 %suppose that transitions looping to the same state does not do assignments.
-Note that we make no assumption on finiteness of the set of states nor
+Note that we make no assumptions on finiteness of the set of states, nor
 on finite branching of the transition relation.
 
-We first define the set of actions a pLTS can use, let $a$
+We first define the set of actions a pLTS can use.  Let $a$
 range over action labels, $\symb{op}$ are operators, and $x_i$ range over
@@
   p_i&::=& ~\symb{Expr}&\text{parameters}\\
-  \symb{Expr}&::=& \symb{Value}~|~x~|~\symb{op}(\symb{Expr}_1,..,\symb{Expr}_n)&\text{Expressions}
+  \symb{Expr}&::=& \symb{Value}~|~x~|~\symb{op}(\symb{Expr}_1,\dots,\symb{Expr}_n)&\text{expressions}
 \end{array}
@@
 \label{pLTS}
+\noteSB{It's a bit strange that algebra presentations are not referred to here}
 A pLTS is a tuple
@@
 \item[$\bullet$]
-$S$ is a set of states.
+$S$ is a set of \emph{states}.
 \item[$\bullet$]
-$s_0 \in S$ is the initial state.
-\item[$\bullet$] $\to \subseteq S \times L \times S$ is the transition relation and 
-$L$ is the set of labels of the form
+$s_0 \in S$ is the \emph{initial state}.
+\item[$\bullet$] $\to \subseteq S \times L \times S$ is the \emph{transition relation}, with
+$L$ the set of labels of the form
 $\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in J}\rangle$,
-where $\alpha \in\AlgA$ is a parameterized action, $e_b \in
-\AlgB$ is a guard, and the variables $x_j\in P$
+where $\alpha \in\AlgA$ is a parameterized action, \noteSB{Shouldn't this be $e_b \in \AlgB_{\mathcal{P}}$, for {\em some} $\mathcal{P}$?}\hl{$e_b \in
+\AlgB$} is a guard, and the variables $x_j\in P$
 are assigned the expressions $e_j\in \AlgE$.
@@
 		$\vars(\alpha)\!\subseteq\! \vars(s)$, 
-		$\vars(e_b)\!\subseteq\! \vars(s')$, and
+		\noteSB{I would expect $\vars(e_b)\!\subseteq\! \vars(s)$, since the guard has to be tested on the source state}\hl{$\vars(e_b)\!\subseteq\! \vars(s')$}, and
 		$\forall j\!\in\! J .\,\vars(e_j)\!\subseteq\! \vars(s)\land 
 x_j\!\in\!\vars(s')$.
-\item[$\bullet$]
-The $x_j$ here are $state\ variables$ of state $s'$.
-
+%\item[$\bullet$]
+The $x_j$ are \emph{state variables} of %% the state
+$s'$. 
 \end{itemize}
@@
 
-Now we define
-pNet nodes, as constructors for hierarchical behavioral structures.
+Now, we define
+pNet nodes as constructors for hierarchical behavioral structures.
 A pNet node has a set of sub-pNets that can be either pNets or pLTSs, and a
-set of Holes, playing the role of process parameters.
-
-A composite pNet consists of a set of sub-pNets exposing
-a set of actions, each of them triggering internal actions in each of
-the sub-pNets. The synchronization between global actions and
-internal actions is given by  \emph{synchronization vectors}: a
-synchronization vector synchronizes one or several internal actions, and
-exposes a single resulting global action.
+set of \emph{holes}, playing the role of process parameters.
+
+A composite pNet consists of a set of sub-pNets, each exposing
+a set of actions. %% , each of them triggering internal actions in each of
+%% the sub-pNets.
+The relation between actions of a pNet and those of its sub-pNets
+%% internal actions is
+are given by  \emph{synchronization vectors}, which %% : a
+%% synchronization vector 
+synchronize one or several internal actions, and
+expose a single resulting global action.
 
 \begin{definition}[pNets]\label{def-pnets}
-A pNet is a hierarchical structure which leaves are pLTSs and holes:\\
-$\pNet\triangleq pLTS~|~\mylangle \pNet_i^{i\in I}, S_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle$
+A pNet is a hierarchical structure, whereof the leaves are pLTSs and holes:
+$\pNet::= pLTS~|~\mylangle \pNet_i^{i\in I}, S_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle$,
 where
 \begin{itemize}
-\item[$\bullet$] $I \in \I$ is the set over which sub-pNets are indexed.
-\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets.
-
-\item[$\bullet$] $J\in\I_\P$ is the set over which holes are indexed.
-$I$ and $J$ are \emph{disjoint}: $I\cap J=\emptyset$,  $I\cup J\neq\emptyset$
+\item[$\bullet$] \noteSB{Why is one $\I$ and the other $\I_\P$?}\hl{$I \in \I$ and $J\in\I_\P$} are the sets over which are indexed sub-pNets and holes, respectively, such that: $I\cap J=\emptyset$ and  $I\cup J\neq\emptyset$.
+
+\item[$\bullet$] $\pNet_i^{i\in I}$ is a family of sub-pNets.
 
@@
 
-\item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
-  synchronization vectors ($K\in\I_\P$). $\forall k\!\in\! K,
-  \symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k$ where
+\item[$\bullet$] $\symb{SV}_k^{k\in K}$, with $K\in\I_\P$, is a set of
+  synchronization vectors: for each $k\!\in\! K$,
+  $\symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k$ where
   $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
-  $\forall i\!\in\! I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$,
+  $\forall i\!\in\! I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$\noteSB{What is the sort of a pNet? Should we define $\Sort(\pNet_i) \triangleq \{\Label(\symb{SV}_k\,|\,k \in K\}$?}, 
   $\forall j\!\in\!
@@
 
-In Fig.~\ref{schema:ArchFailure:pNet} we show examples of these
-constructs, with 2 pLTSs and one pNet node encoding our use-case.
+In Fig.~\ref{schema:ArchFailure:pNet}, we show examples of these
+constructs, with two pLTSs, one hole and one pNet node encoding our running example.
 
@@
   architectures.  Future work may include automatic synthesis of
-  architectures from, \eg[,] CTL~\cite{BaierKatoen2008} formulae.
+  architectures from, \eg CTL~\cite{BaierKatoen2008} formulae.
 %
@@
 %
-Adding priorities $\NameOprnd.\PortFinish < \NameCtrl.\PortReset$ and
-$\NameOprnd.\PortFinish < \NameOprnd.\PortResume$, ensures that, after
-a failure, the operation performed by $\NameOprnd$ cannot finish
-unless it is explicitly resumed or the system is reset.
+%% Adding priorities $\NameOprnd.\PortFinish < \NameCtrl.\PortReset$ and
+%% $\NameOprnd.\PortFinish < \NameOprnd.\PortResume$, ensures that, after
+%% a failure, the operation performed by $\NameOprnd$ cannot finish
+%% unless it is explicitly resumed or the system is reset.
 
@@
 \[
-\varphi \land \mathtt{AG} (\PortReset \rightarrow \varphi)\,,
-\quad\text{where}\quad
+\varphi \land \mathtt{AG} (\PortReset \rightarrow \varphi),
+\quad\text{where}\
 %
 \varphi = \mathtt{A} [\lnot \PortReset\ \mathtt{W}\ \PortAsk]
-\land \mathtt{A} [\lnot \PortAsk\ \mathtt{W}\ \PortFail]
+\land \mathtt{A} [\lnot \PortAsk\ \mathtt{W}\ \PortFail],
 \]
@@
 %
-
-\TODO{it would be good to express here maybe 2 properties of the
-  architecture, maybe one taken from the original study, and another
-  one involving the timer data (number of ticks ?)}
+The satisfaction of the safety property could be established by
+applying symbolic model checking techniques.  However, in this
+example, it is obvious by inspection of the open automaton.  The
+satisfaction of the liveness property relies on the above observation
+that in the state $\ostate{s2,t0}$ only the reset transition involves
+$\NameCtrl$.  Therefore, under resonable scheduling assumptions,
+$\PortReset$ will always be fired.
+
+%% \TODO{it would be good to express here maybe 2 properties of the
+%%   architecture, maybe one taken from the original study, and another
+%%   one involving the timer data (number of ticks ?)}
 
@@
 
-In this paper we presented the algorithm for generating an open
-automaton representing the semantics of an open pNet, and we described
-the implementation of the
-algorithm. Our implementation includes two main parts. First, we
-compute all the possible open transitions. The actions in pLTS and
-hole behaviors are composed in the algorithm while the generation of
+In this paper, we presented an algorithm for generating an open
+automaton representing the semantics of an open pNet.
+We have also presented our implementation, which comprises two main parts. Firstly, we
+compute all the possible open transitions.
+\noteSB{I do not understand this sentence.
+Suggestion: The actions of pLTS and hole behaviours are composed by the algoritm during the generation of predicates needed to match...(?)}\hl{The actions in pLTS and
+hole behaviors are composed in the algorithm, while the generation of
 predicate need to match the combinations of the subnets with the
-synchronization vectors. Some of the open transitions obtained at this
+synchronization vectors.}  Some of the open transitions obtained at this
 intermediate step, constructed in a structural manner from all
@@
 instantiations. 
-To get rid of these useless transitions, we use the SMT solver Z3 for checking the
-satisfiability of the predicate in each open transition. In
-order to do that, we encode into Z3 the action algebra presentation,
-the a representation of the predicates, before submitting them to the
-Z3 solver. We implemented our algorithm in the VerCors platform and use some
-running examples, encoding expressions from various process algebras, to test the
-algorithm. Our use-cases show that our encoding
-identifies successfully all unsatisfiable open transitions and that
-the resulting automaton reflects correctly the expected 
+Secondly, to get rid of these useless transitions, we use the SMT solver Z3 for checking the
+satisfiability of the predicate in each open transition. 
+To this end, we encode into Z3 the representations of the action algebra and
+the predicates before submitting them to the
+Z3 solver. We implemented our algorithm in the VerCors platform and 
+tested the algorithm on available examples, such as encoding expressions from various process algebras. Our case-studies show that our encoding
+successfully identifies all unsatisfiable open transitions and that
+the resulting automata correctly reflect the expected 
 movements of the encoded process expressions.
 
-Among the questions arising during this work, an important one is the
-efficiency of Z3 for our needs. Z3 is famous for being very fast for
-solving very large sets of assertions, and this could be important for
-us. But we encountered  some problems during the implementation the
-checking method using Z3. For example, if the $functions$ and the
-$datatypes$ part of the algebra presentation we submit to the solver
-are independent with each other, then checking the $assertions$ is a
-simple work. However, $functions$ on recursive $datatypes$ make it
-more complex, some special rules might be defined by user for the
+Among the questions that have arised during this work, an important one is the
+efficiency of Z3 for our needs. Z3 is famous for being very fast in
+solving very large sets of assertions.%% , which could be important for
+%% us
+However, we encountered problems during the implementation of the
+checking method using Z3. For example, if the $\mathit{functions}$ and the
+$\mathit{datatypes}$ part of the algebra presentation that we submit to the solver
+are independent from each other, then checking the $\mathit{assertions}$ is 
+simple. However, $\mathit{functions}$ on recursive $\mathit{datatypes}$ make it
+more complex. Special rules might be defined by the user for the
 induction. Also, we need more evidence that dealing with more complex
-action algebras, that would involve axiomatizing their data structures
+action algebras, which would involve axiomatizing their data structures
 into Z3 theories, will indeed allow us to decide validity of
@@
 predicates on data) seems easy to define, equivalence checking is more challenging.
-In previous paper, we
-have already found the FH-bisimulation, inspired by~\cite{deSimone85} as a
-suitable definition. But usual approaches of bisimulation by partition
+In a previous paper~\hl{\cite{x}}, we
+have already found the FH-bisimulation, inspired by~\cite{deSimone85}, to be a
+suitable definition. However, the usual approach of computing bisimulation by partition
 refinement does not work easily with symbolic transitions. In a first
@@
 		\hline\specialrule{0em}{1pt}{1pt}
-		Sort & Constructors & Other Operators
+		Sort & Constructors & Auxiliary Operators
                 \\\hline\specialrule{0em}{1pt}{1pt} 
@@
 		&       		\\\specialrule{0em}{5pt}{5pt}
-		\multispan{2} (Binary operators, e.g.: $\land, \lor$ for booleans, $+, -, \times, \div, \le, \ge$ for integers, etc.)
+		\multispan{2} (Binary operators, e.g.: $\land, \lor$ for Booleans, $+, -, \times, \div, \le, \ge$ for integers, etc.)
 
@@
 		&       		\\\specialrule{0em}{3pt}{3pt}
-		\multicolumn{2}{l}{(Unary operators, e.g. $\lnot$ for booleans, - for integers)}
+		\multicolumn{2}{l}{(Unary operators, e.g. $\lnot$ for Booleans, - for integers)}
 
@@
 and selectors as \texttt{declare-datatypes}, and the declaration of
-other operators as \texttt{declare-function} constructs.
+auxiliary operators as \texttt{declare-function} constructs.
 For sorts, we must distinguish the case of mutually defined sorts
@@
 		&&       		\\\specialrule{0em}{1pt}{1pt}
-		\multicolumn{2}{l}{Other operators: }
+		\multicolumn{2}{l}{Auxiliary operators: }
 
@@
 
-% \TODO{This is incomplete... Xudong: Conjunctive normal form, translation function for boolean expressions, + assignments}
+% \TODO{This is incomplete... Xudong: Conjunctive normal form, translation function for Boolean expressions, + assignments}
 

### 2018-01-19 2017-Xudong-SMT/FM-2018-extended.tex
Minor modifications -- 15 pages now

@@
 \newcommand{\noteInSB}[2][inline,color=green!40]{\todo[#1]{{\bf Simon: } {#2}}}
+\newcommand{\todoMargin}[2][color=red!60, size=\tiny]{\todo[#1]{{\bf
+      ToDo: } {#2}}}
 
@@
   $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
-  $\forall i\!\in\! I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$\noteSB{What is the sort of a pNet? Should we define $\Sort(\pNet_i) \triangleq \{\Label(\symb{SV}_k\,|\,k \in K\}$?}, 
+  $\forall i\!\in\! I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$\noteSB{What is the sort of a pNet? Should we define $\Sort(\pNet) \triangleq \{\Label(\symb{SV}_k\,|\,k \in K\}$?}, 
   $\forall j\!\in\!
@@
 
-In appendix \ref{appendix:mapsmt} we formally define the translation of each
+In App.~\ref{appendix:mapsmt} we formally define the translation of each
 open transition, including:
@@
 
-In Fig.~\ref{schema:smt-lib} you can see the decomposition of the
+Figure~\ref{schema:smt-lib} shows the decomposition of the
 predicate into a set of asserts, each encoding an elementary equality,
-inequality, or a guard. The final command in the translation is a
-\texttt{(check-sat)}, which result (sat or unsat) will be decoded by
+inequality, or a guard. 
+The result (sat or unsat) of the final command in the translation (\texttt{check-sat}) is decoded by
 our algorithm.
@@
 efficiency of Z3 for our needs. Z3 is famous for being very fast in
-solving very large sets of assertions.%% , which could be important for
+solving very large sets of assertions. %% , which could be important for
 %% us
 However, we encountered problems during the implementation of the
-checking method using Z3. For example, if the $\mathit{functions}$ and the
+checking method. %% using Z3. 
+For example, if the $\mathit{functions}$ and the
 $\mathit{datatypes}$ part of the algebra presentation that we submit to the solver
@@
 more complex. Special rules might be defined by the user for the
-induction. Also, we need more evidence that dealing with more complex
+induction.  We need more evidence that dealing with more complex
 action algebras, which would involve axiomatizing their data structures
-into Z3 theories, will indeed allow us to decide validity of
+as Z3 theories, will allow us to decide validity of
 predicates.
@@
 
-\TODO{Change perspective: we are working on the formal extension of
-  BIB architectures, and their semantics in terms of pNets. Then
+\todoMargin{Change perspective: we are working on the formal extension of
+  BIP architectures, and their semantics in terms of pNets. Then
   bisimulation and model-checking principles adapted to open pNet
   systems are under development}
-
+%
 Naturally, our next goals after the generation of the open automata

### 2018-01-20 2017-Xudong-SMT/FM-2018-extended.tex
Minor: rearranged slightly the formula defining the Matching predicate
More proof-reading

@@
 %% SB: Moved the macro definitions from XFIG/figtex2eps-preamble.tex
-%%     to XFIG/macros.tex and added a com and to input this latter one
+%%     to XFIG/macros.tex and added a command to input this latter one
 %%     into the paper source (above in this file).
@@
 %\newcommand\ostate[1]{\triangleleft{#1}\triangleright}
+
 \newcommand{\sm}[1]{\mbox{\boldmath\small #1}}
@@
 is an automaton where each transition composes transitions 
-of several LTSs with the
+of several \noteSB{These should all be pLTSs, right? Or did I miss something?}\hl{LTSs} with the
 actions of some holes; the transition occurs if some predicates hold,
 and can involve a set of state modifications. Each state of an open
-automaton has a set of \emph{state variables} that can be assigned
+automaton has a set of \emph{state variables} that can be assigned by
 incoming transitions.
@@
 	\label{def:OpenTransitions}
-	An \emph{open transition} over a set  $(S_i,s_{0 i}, \rightarrow_i)^{i\in
-	I}$ of LTSs, a
+	An \emph{open transition} over a set  $\langle S_i,s_{0 i}, \rightarrow_i\rangle^{i\in
+	I}$ of \hl{LTSs}, a
 	set $J$ of holes with sorts $Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is a structure of the form:	
@@
 	{\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
-		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred, \Post}
-	{s \xrightarrow {v}s'}
+		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred\,, \Post}
+	{s \xrightarrow {v}s'}\,,
 	\end{mathpar}
-	Where $s, s'\in\mathcal{S}$ and for all
+	where $s, s'\in\mathcal{S}$ and, for all
         $i\in I$, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the
-	LTS $(S_i,s_{0 i}, \rightarrow_i)$, and $\xrightarrow{b_j}_j$
+	\hl{LTS} $\langle S_i,s_{0 i}, \rightarrow_i\rangle$, and $\xrightarrow{b_j}_j$
         is a transition of the hole $j$, for any action $b_j$ in the
@@
         substitution $\{x_k\gets e_k\}^{k\in K}$  
-	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are
+	where $x_k$ are variables of $s'$ and $s'_i$, whereas $e_k$ are
         expressions over the other variables of the open transition.
@@
 	An \emph{open automaton} is a structure\\ $A =
-	<LTS_i^{i\in I},J,\mathcal{S},s_0,\mathcal{T}>$ where:
+	\langle \mathit{LTS}_i^{i\in I},J,\mathcal{S},s_0,\mathcal{T}\rangle$ where:
 	\begin{itemize}
 		\item[$\bullet$]  $I$ and $J$ are  sets of indices,
-		\item[$\bullet$]  $LTS_i^{i\in I}$ is a family of LTSs,
-		\item[$\bullet$]   $\mathcal{S}$ is a set of states and $s_0$ an initial state
-		among $\mathcal{S}$,
-		\item[$\bullet$] $\mathcal{T}$ is a set of open transitions and for each
-		$t\in \mathcal{T}$ there exist $I'$, $J'$ with $I'\subseteq I$, $J'
+		\item[$\bullet$]  \noteSB{And one more above}\hl{$LTS_i^{i\in I}$} is a family of \hl{LTSs},
+		\item[$\bullet$]   $\mathcal{S}$ is a set of states and $s_0 \in \mathcal{S}$ the initial state,
+		\item[$\bullet$] $\mathcal{T}$ is a set of open transitions and, for each
+		$t\in \mathcal{T}$, there exist $I'$, $J'$ with $I'\subseteq I$, $J'
 		\subseteq J$, such that $t$ is an open transition over $LTS_i^{i\in I'}$, $J'$,
@@
 % \TODO{Relate to the algorithm, or even move to section 5}
-When building an Open Automaton as the semantics of a pNet, its
-\emph{states}, and the shape of the \emph{predicates} in its
-transitions have a specific structure:
-
-\paragraph{States of open pNets:}\label{def-states}
+The \emph{states} and the shape of \emph{predicates} in the
+transitions
+of an open automaton representing the semantics of a pNet
+have the following specific structure.
+
+\paragraph{States of open pNets.}\label{def-states}
   A state of an open pNet is a tuple of the
@@
   in structured states as $\triangleleft\ldots\triangleright$).
-  For any pNet p, let $\overline{Leaves} = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be the set of pLTS at its leaves,
-  then $States(p) = \{\triangleleft s_i^{i\in L}
-  \triangleright| \forall i\in L. s_i \in S_i\}$.
+  For any pNet p, let $\overline{\mathit{Leaves}} = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be the set of pLTS at its leaves,
+  then $\mathit{States}(p) = \{\ostate{s_i^{i\in L}}
+  |\, \forall i\in L. s_i \in S_i\}$.
 A pLTS being its own single leave:
-  $States(\mylangle S,s_0, \to\myrangle) = \{\triangleleft s \triangleright| s \in S\}$.
+  $\mathit{States}(\mylangle S,s_0, \to\myrangle) = \{\ostate{s}|\, s \in S\}$.
 The initial state is defined as:
-$InitState(p) = \triangleleft {{s_i}_0}^{i\in L}  \triangleright$.
+$\mathit{InitState}(p) = \ostate{{{s_i}_0}^{i\in L}}$.
 
@@
 
-\paragraph{Predicates:}
+\paragraph{Predicates.}
 Let
@@
 the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
-\[\MkPred(SV_k, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow
-\begin{array}{l}
+\begin{multline*}
+  \MkPred(SV_k, a_i^{i\in I}, b_j^{j\in J}, v)\Longleftrightarrow
+  %% \begin{array}{l}
   \exists {(a'_i)}^{i\in I},
-{(b'_j)}^{j\in J},v'.\, SV_k={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v'
-\\~~\land
+          {(b'_j)}^{j\in J},v'.\\
+          SV_k={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v'
+          \land
           \forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v'
-\end{array}\]
+\end{multline*}
+
+%% \end{array}
 
@@
 
-\begin{example}\emph{An open transition.}
-  This transition is generated by application of vector \texttt{SV0},
-  synchronizing the initial actions of pLTSs \texttt{Failure} and
-  \texttt{Timer}, with an action of the hole \texttt{B} equal to
+\begin{example}[An open transition]
+  This transition is generated by application of the vector \texttt{SV0},
+  synchronizing the initial actions of pLTSs \texttt{Control} and
+  \texttt{Timer} (see Fig.~\ref{schema:ArchFailure:pNet}), with an action of the hole \texttt{B} equal to
   \texttt{fail}. The local variable \texttt{t} of the \texttt{Timer}
   is assigned to its initial value \texttt{Max}.
-In fact this OT is displayed in a simplied, human readable form. The
+\noteSB{This is the first mention of the tool\mdash I would move this text much further.}\hl{In fact this OT is displayed in a simplied, human readable form. The
 raw output of the tool is slightly more difficult to read, in
@@
 appendix~\ref{appendix:variables}). A full output of 
-the use-case is provided in appendice~\ref{appendix:fullOutput}.
+the use-case is provided in appendice~\ref{appendix:fullOutput}.}
 
@@
 	\inferrule*[myfraction=\reddottedrule]
-	{\{s0~{\xrightarrow{fail(true)}} ~s1, t0~{\xrightarrow{start(true)}} ~t1\}
-	  \{\xrightarrow{hb}\}, hb=fail(true) \land v=\underline{fail}, \{t := Max\}
+	{\{s0~{\xrightarrow{\mathit{fail}(\true)}} ~s1, t0~{\xrightarrow{\mathit{start}(\true)}} ~t1\}
+	  \{\xrightarrow{\mathit{hb}}\}, \mathit{hb}=\mathit{fail}(\true) \land v=\underline{\mathit{fail}}, \{t := \mathit{Max}\}
         }
@@
 \cite{henrio:Forte2016}, in the form of 2 structural rules, one for
-pLTSs, one for pNet nodes.. For convenience we include these rules in
-appendix \ref{appendix:semRules}.
+pLTSs, one for pNet nodes.  For convenience we include these rules in
+App.~\ref{appendix:semRules}.
 
@@
 
-Our algorithm starts with an open pNet, and builds its set of open
+\noteSB{$E$ is never updated, so $E = \emptyset$}
+Algorithm~\ref{alg1} starts with an open pNet, and builds its set of open
 transitions. Its main loop is a classical residual algorithm: starting
@@
 \Require The pNet node P.
-\State Initialize sets $U=InitSate(P)$, $E=\emptyset$ for unexplored/explored global states, $L$ for result OTs;
-\While{!isEmpty(U)}
-	\State Chose $S$ in $U$;
-	\State OT = MakeTransitions(P, S);
-        \State Store $OT$ in $L$; 
-	\For{each target global state $T$ from $OT \in L$}
-		\IfThen{$(!U.contains(T))\ \&\&\ (!E.contains(T))$}{Add $T$ into the $U$;}
+\State Initialize sets $U=\mathit{InitState}(P)$, $E=\emptyset$ for unexplored/explored global states, $L=\emptyset$ for the resulting OTs;
+\While{!$\mathit{isEmpty}(U)$}
+	\State Choose $S$ in $U$;
+	\State $\mathit{OT} = \mathit{MakeTransitions}(P, S)$;
+        \State Store $\mathit{OT}$ in $L$; 
+	\ForAll{$\mathit{OT} \in L$}
+        \State Let $T$ be the target global state of $\mathit{OT}$
+	\IfThen{($T \not\in U$ \&\& \hl{$T \not\in E$})}{Add $T$ into $U$;}
 	\EndFor
@@
 \State Prune the open transitions in $L$ using the SMT solver;
-\State \Return $OA=Reachable(InitState(P),L)$;
+\State \Return $\mathit{OA}=\mathit{Reachable}(\mathit{InitState}(P),L)$;
 
@@
 the semantic rules following the structure of the pNet. 
-For pLTS at leaves, we simply take the pLTS transitions of the
+For pLTSs at the leaves, we simply take the pLTS transitions of the
 corresponding local state and build the predicate to generate the
@@
 hierarchical manner.
-
+%
 Then, at the root of the pNet, the predicate of each OT is translated
@@
 predicate: 
-
-$$Matching(SV_k, C_n, Hole, v) = 
-\begin{array}{l}
+%
+\begin{multline*}
+  \mathit{Matching}(SV_k, C_n, \mathit{Hole}, v) = 
+  \\
   \forall {(a'_i)}^{i\in I},
-{(b'_j)}^{j\in J},v'.
-\\
+          {(b'_j)}^{j\in J},v'.\
           v_i=a'_i\land \, b_j=b'_j \land v=v' \land G_k
-\end{array}$$
+\end{multline*}
 
@@
     \OTland (b_1\lor b_2) \Rightarrow b_0, ~~\{\}}
-    	   {\ostate{s1,t1} \xrightarrow{v} \ostate{s1,t0}}\\
+    	   {\ostate{s1,t1} \xrightarrow{v} \ostate{s1,t0}}
   \end{mathpar}

### 2018-01-22 2017-Xudong-SMT/FM-2018-extended.tex
Finished proof-reading -- many comments

@@
 
-\noteSB{$E$ is never updated, so $E = \emptyset$}
+\noteSB{line 8: $E$ is never updated, so $E = \emptyset$ always;\\
+line 11: Would it not be better to prune unsatisfiable transitions on-the-fly, \ie inside the loop?}
 Algorithm~\ref{alg1} starts with an open pNet, and builds its set of open
@@
 \EndWhile
-\State Prune the open transitions in $L$ using the SMT solver;
+\State \hl{Prune the open transitions in $L$ using the SMT solver;}
 \State \Return $\mathit{OA}=\mathit{Reachable}(\mathit{InitState}(P),L)$;
@@
 the semantic rules following the structure of the pNet.
-For pLTSs at the leaves, we simply take the pLTS transitions of the
+\hl{For pLTSs at the leaves, we simply take the pLTS transitions of the
 corresponding local state and build the predicate to generate the
-open transition. 
+open transition.}
 On a pNet node we use two methods, combining and
@@
 
+%
+\noteInSB{Algorithm~\ref{alg2}, as presented below is not
+  well-defined: when we reach the leaves, a pLTS does not have any
+  subnets, hence the loop in lines 2--4 is empty and so is the list
+  $l$. $\mathit{Combining}(l)$ is then called on an empty list...}
+
+\noteInSB{Line 2: Tr1 and Tr2 are the semantic rules, right?}
+
+\noteInSB{Line 6: Nothing in the assignment $\overline{comb} =
+  \mathit{Combining}(l)$ depends on $sv$.  Hence, this should probably
+  be done outside of the loop.}
+
+\noteInSB{Line 7: There are two type mismatches here: $ot$ is an open
+  transition, whereas $\mathit{Matching}$ is a predicate\mdash one
+  cannot assign a predicate to an open transition.  Furthermore, in
+  the definition of $\mathit{Matching}$, below, $C_n$ is an open
+  transition, whereas $\overline{comb}$ is a {\em set} of open
+  transitions, so this call does not type either. There is probably
+  another inner loop over all tuples of OTs in $\overline{comb}$; even
+  so the open transition has to be defined completely, not just the
+  predicate\mdash what is the value of $Post$ for the new transition?
+  Maybe $\mathit{Matching}$ should not be a predicate, but an OT?
+  Finally, how is $\mathit{hole}$? (I have removed $v$\mdash here and
+  in the parameters of the definition of the $\mathit{Matching}$
+  predicate, because the text in the paragraph ``Matching'' says that
+  $v$ is fresh.)}
+
+\noteInSB{Line 8: When is $\mathit{Filter}(ot)$ called?}
+
 \begin{algorithm}
@@
 \begin{algorithmic}[1]
-\Require a pNet node Pn; a global state S.
-\State Initialize a list $l$, $L$ for sub-transitions/transitions.
-	\For{each Subnet in Pn}
-	~~~ $\setminus \setminus$ Recursively applying Tr1 or Tr2 on the sub-nodes.
-                \State Store MakeTransitions(Subnet, S) in $l$;
+\Require a pNet node $Pn$; a global state $S$.
+\State Initialize empty list $l$ and set $L$ for sub-transitions/transitions.
+	\For{each $\mathit{Subnet}$ in $Pn$}
+	~~~ $\setminus \setminus$ Recursively applying \hl{Tr1 or Tr2} on the sub-nodes.
+                \State Store $\mathit{MakeTransitions}(Subnet, S)$ in $l$;
 	\EndFor
 	\For{each $sv \in SV$}
-		\State $\overline{comb} = Combining(l)$;
-                 \State $ot = Matching(sv, \overline{comb}, hole, v)$;
-                 \State Store $ot$ in $L$; ~~~ $\setminus \setminus$ if Filter(ot) succeeds
+		\State $\overline{comb} = \mathit{Combining}(l)$;
+                 \State \hl{$ot = \mathit{Matching}(sv, \overline{\mathit{comb}}, \mathit{hole})$;} % SB: removed the fourth parameter v here
+                 \State Store $ot$ in $L$; ~~~ \hl{$\setminus \setminus$ if $\mathit{Filter}(ot)$ succeeds}
 	\EndFor
@@
 \def\inactive{\{-\}}
-\paragraph{Combining:}
-The combining method enumerate all the possible behaviours of the
+\paragraph{Combining.}
+The combining method enumerates all the possible behaviours of the
 subnets, as all the possible combinations of their open transitions.
-Assume that there is a collection of $n$ subnets
-$L = {s_1, s_2, ...,  s_n}$; we denote $\overline{ot}_i$ the set of open
-transitions of the 
-subnet $s_i$ and ``$-$'' means the subnet is not involved;
-then the combination $\overline{comb}$, a set of n-tuples, is the
-cartesian product of sets :  
-$\overline{comb} : (\inactive\cup \overline{ot}_1) \times (\inactive\cup \overline{ot}_2)\times ... \times (\inactive\cup \overline{ot}_n).$
+Assume that there is a collection of $n$ subnets.\noteSB{These variables are not used and conflict with the returned set $L$ in Alg.~\ref{alg2}, on one hand, and control states $s_i$ of the subnets, on the other.}\st{
+$L = {s_1, s_2, ...,  s_n}$;} We denote $\overline{ot}_i$ the set of open
+transitions of the $i$-th
+subnet; %% $s_i$ and 
+``$-$'' means that the subnet is not involved.
+The combination $\overline{comb}$, a set of n-tuples, is the
+cartesian product:  
+$\overline{comb} = (\inactive\cup \overline{ot}_1) \times (\inactive\cup \overline{ot}_2)\times \dots \times (\inactive\cup \overline{ot}_n)$\hl{, where, for each $i \in [1, n]$, $\overline{ot}_i$ is the set of open transitions obtained from the $i$-th subnet in line~3 of the algorithm}.
 
@@
 
-\paragraph{Matching:}
+\paragraph{Matching.}
 The next step, for each synchronisation vector, and each possible
 combination of behaviour of the subnets as generated by the \emph
-{Combining} method, consists in building the combined predicate,
+{Combining} method, consists in building the combined predicate
 and the corresponding open transition.
-From a synchronization vector
-$sv_k\in SV = (a'_i)^{i\in I} (b'_j)^{j\in J}\rightarrow v'$
-and its guard $G_k$, a tuple of open transitions
-$C_n\in \overline{comb} = {(v_i)}^{i\in I}$, the hole behaviors $Hole$,
-and a fresh variable representing the result action $v$, we build the
-predicate: 
+\hl{From a synchronization vector
+$sv = \left((a'_i)^{i\in I} (b'_j)^{j\in J}\rightarrow v'\right) \in SV$
+and its guard $G_k$; a tuple of open transitions
+$C = ({ot}_i)^{i \in [1,n]} \in \overline{comb}$, such that, for each $i \in [1,n]$, either $ot_i = -$, or the result action of $ot_i$ is $a_i$; the hole behaviors $\mathit{Hole} = (b_j)^{j \in J}$; and a fresh variable $v$, representing the result action of the OT under construction, we build the predicate}
 %
 \begin{multline*}
-  \mathit{Matching}(SV_k, C_n, \mathit{Hole}, v) = 
+  \mathit{Matching}(sv, C, \mathit{Hole}) = 
   \\
-  \forall {(a'_i)}^{i\in I},
-          {(b'_j)}^{j\in J},v'.\
-          v_i=a'_i\land \, b_j=b'_j \land v=v' \land G_k
+  (\forall i\in I, a_i=a'_i) \land
+  (\forall i \not\in I, ot_i = -) \land
+  (\forall j\in J, b_j=b'_j) \land
+  (v=v') \land G_k.
 \end{multline*}
 
-\paragraph{Filtering:}
+\paragraph{Filtering.}
 There may be several reasons why such a matching would fail:
@@
   \item if some subnet action expression in the vector does not match (by
-    pattern-matching) the corresponding behaviour $C_n$,
+    pattern-matching) the corresponding \hl{action in $C$},
   \item or if the whole set of active subnet actions in the vector
-    cannot be matched (by unification) with the set $\{C_n\}$.
+    cannot be matched (by unification) with \hl{the tuple $C$}.
 \end {itemize}
 
-Each of these possible filters is more precise than the previous
-ones. But even when unification succeeds, it is still possible that
+\st{Each of these possible filters is more precise than the previous
+ones. But e}Even when unification succeeds, it is still possible that
 the resulting predicate would be unsatisfiable, because of some
@@
 that assign potentially different values to a state variable.
-To handle such cases, the algorithm manages for each pLTS state, as a
+To handle such cases, the algorithm manages, for each pLTS state, a
 list of expressions collected from the assignments of each state
-variable $v$.
+variable. %% $v$.
 %% The list we used contains triples <$v$, $S$, $AssignRH$> 
@@
 For a global state in the open automaton, getting the set of state
-variables (which may be used in a transition) will simply be the union
-of state variables of the individual pLTS states constituting this
+variables (which may be used in a transition) %% will simply be
+\hl{is realised by taking
+the union
+of sets of} state variables of the individual pLTS states constituting this
 global state (variables of different pLTS are distinct).
@@
 the predicates express incompatible constraints. Even if having an
-unsatisfiable (symbolic) transition in the open automaton would not be incorrect,
-we want to check them for satisfiability, and reduce the number of
-transitions and states in the automaton.
-In Fig.~\ref{schema:unsat-ot}, we display an example of an
+unsatisfiable (symbolic) transition would not be incorrect,
+\hl{we choose to minimize the open automaton (\ie its number of
+transitions and states), by checking these predicates} for satisfiability.
+In Fig.~\ref{schema:unsat-ot}, we show an 
 unsatisfiable open transition 
-from the result of our example. It shows the case where
-the failure controller performs a ``$fail$'' action, while the timer
-executes a ``$resume$''. The chosen synchronization
+from the open automaton of our running example. It shows the case where
+the failure controller performs a ``$\PortFail$'' action, while the timer
+executes a ``$\PortResume$''. The chosen synchronization
 vector (SV0 from Fig.~\ref{schema:ArchFailure:pNet}) does not match
-with these actions, as shown by the predicate
-fragment ``resume(true)=start($b_2$)''.
+with these actions, \hl{since it expects $\NameTimer.\PortStart$. This mismatch is materialised} %% as shown
+by the predicate
+fragment ``$\mathit{resume}(\true)=\mathit{start}(b_2)$''.
 
@@
 Checking satisfiability requires some symbolic computation
-on the action expressions and the predicates, and this 
+on the action expressions and the predicates, which
 may depend on the specific theory of the action algebra datatypes. 
@@
 using the SMT solver Z3. More precisely, we translate
-the OT predicate into a SMTlib assertion, in the context provided by
+the OT predicate into an SMTlib assertion in the context provided by
 the possible state variable assignments in the source state. In this
-section we describe the translation of the algebra presentation, of
+section, we describe the translation of the \noteSB{The algebra presentation only appears here for the first time after its definition in Sect.~\ref{section:pnets}}\hl{algebra presentation}, of
 assignments, and of the predicates.
 
-From inside our algorithm code, we submit satisfiability requests to
-Z3 using its JAVA API. Here for readability, we
+Our implementation submits satisfiability requests to
+Z3 using its JAVA API. Here, for readability, we
 show the Z3 code using its SMT-LIB input language.
@@
 Here we display also the proof generated by Z3,
-though in practice our tool only needs the brute information ``sat''
-or ``unsat''. The result "unsat" in the output is just what we expected.
+\noteSB{I am not sure I understand the entire message of this phrase}\hl{though in practice our tool only needs the brute information ``sat''
+or ``unsat''. The result "unsat" in the output is just what we expected.}
 % as appears in the ``unsat'' proof generated by Z3 in which ``\{= ?x66 ?x70\}'' is shown to be false (see Fig. \ref{schema:smt-lib})
@@
 To build the input submitted to Z3 for each OT,
-we translate the algebra $presentation$, the predicates and the
+we translate the algebra presentation, the predicates and the
 variable assignments (the Post part) into Z3 (Java-API) syntax.
@@
 
-\paragraph{Translation of Action algebra presentation}
-In appendix \ref{appendix:mapsmt} we define formally a condition of
-well-formness of an algebra presentation, and its translation into
+\paragraph{Translation of action algebra presentation.}
+In App.~\ref{appendix:mapsmt}, we formally define the condition of
+well-formedness of an algebra presentation, and its translation into
 SMTlib declarations (\texttt{declare-datatypes} and
@@
 and will not raise runtime errors in the SMT engine. Remark that the
-\texttt{declare-datatypes} command include both the Action
-constructors from table \ref{table:BIPalgebra}, but also the constant action
+\texttt{declare-datatypes} command comprises both the action
+constructors from table \ref{table:BIPalgebra} and also the constant action
 names from our example.
 
-\paragraph{Translating assignments into predicate terms}
+\paragraph{Translating assignments into predicate terms.}
 State variable assignments that were collected during the open
 automaton are used when generating the SMTlib asserts (see
-appendix~\ref{appendix:translating-assignments}). This appears in
-Fig.~\ref{schema:smt-lib} in line 10, that encodes possible values of
-the variable $t$ of the timer.
+App.~\ref{appendix:translating-assignments}). \noteSB{I am not an expert of Z3 or SMT-LIB, but the clause '\texttt{(= t (- t 1))}' looks very suspicious to me.}\hl{This appears in
+line 10 of Fig.~\ref{schema:smt-lib}, which encodes possible values of
+the variable $t$ of the timer.}
 
@@
 
-\paragraph{Checking satisfiability}
-
-In App.~\ref{appendix:mapsmt} we formally define the translation of each
+\paragraph{Checking satisfiability.}
+
+In App.~\ref{appendix:mapsmt} we formally define all steps of the translation of each
 open transition, including:
-- collect all variables in the transition, and declare them,
-- check well-formness and correct typing of expressions
-- translate the predicate into a conjunction of assertions
-- if present in the source state, translate the state-variable
+%
+\begin{itemize}
+\item collect all variables in the transition, and declare them,
+\item check well-formedness and correct typing of expressions,
+\item translate the predicate into a conjunction of assertions,
+\item if present in the source state, translate the state-variable
   assignments into a disjunctive assertion.
+\end{itemize}
+%
 Here again, this translation ensures that no runtime error will occur

### 2018-01-22 2017-Xudong-SMT/FM-2018-extended.tex
Resolved one of my earlier comments in the Conclusion.

@@
 compute all the possible open transitions.
-\noteSB{I do not understand this sentence.
-Suggestion: The actions of pLTS and hole behaviours are composed by the algoritm during the generation of predicates needed to match...(?)}\hl{The actions in pLTS and
-hole behaviors are composed in the algorithm, while the generation of
-predicate need to match the combinations of the subnets with the
-synchronization vectors.}  Some of the open transitions obtained at this
+\hl{The algorithm combines the actions of subnets and
+hole behaviors, which are then matched with the
+synchronization vectors by the generated
+predicate.}  Some of the open transitions obtained at this
 intermediate step, constructed in a structural manner from all

### 2018-01-22 2017-Xudong-SMT/FM-2018-extended.tex
def pLTS

@@
 \def\AlgB{\mathcal{B}}
-\def\AlgI{\mathcal{I}}
+%\def\AlgI{\mathcal{I}}
 
@@
 %\DeclareMathOperator{\Flat}{Flat}
-\renewcommand{\P}{\mathcal P}
 \usepackage{listings}
@@
 
+\renewcommand{\P}{\mathcal V}
 \def\Talg{\mathcal{T}_{\Sigma,\P}}
@@
 
+\def\APres{\mathcal{P}}
 \begin{definition}
-  An \emph{algebra presentation} is a triple $\mathcal{P}=\langle\mathit{Sorts},\mathit{Constrs},\mathit{Ops}\rangle$, where
+  An \emph{algebra presentation} is a triple $\APres=\langle\mathit{Sorts},\mathit{Constrs},\mathit{Ops}\rangle$, where
 
@@
   \end{itemize}
-  \noteSB{I think this can be removed}\hl{All sorts and operator names must be distinct.}
+%  \noteSB{I think this can be removed}\hl{All sorts and operator names must be distinct.}
   Among constructors, those of arity 0 are called \emph{constants}:
-  $\mathit{Consts}(\mathcal{P}) = \{\mathit{Con} \in \mathit{Constrs}\,|\, \mathit{arity}(\mathit{Con})=0\}$.
+  $\mathit{Consts}(\APres) = \{\mathit{Con} \in \mathit{Constrs}\,|\, \mathit{arity}(\mathit{Con})=0\}$.
 \end{definition}
@@
 pNet.
+
+The definition of an Algebra Presentation, and a set of variables
+$\P$ fixes the Term algebra elements $\Talg, \AlgB_{\P}, \AlgA_\P$.
 
@@
 which can only be modified by the assignment in transitions targeting this state. 
-A global state variable of a pLTS is a variable $x$ satisfying $\forall s\!\in\! S .\, x\!\in\! \vars(s)$.
+A global state variable of a pLTS is a variable $x$ satisfying
+$\forall s\!\in\! S .\, x\!\in\! \vars(s)$. 
 %
@@
 
-%% \QIN{
-%% [The input variables in an action term are those marked with a
-%% $\symb{?}$.
-%% We additionally suppose that each input variable does not
-%% appear somewhere else in the same action term:
-%% $p_i=?x\Rightarrow\forall j\neq i.\, x\notin \vars(p_j)$]}
-
 \begin{definition}[pLTS]
 \label{pLTS}
-\noteSB{It's a bit strange that algebra presentations are not referred to here}
-A pLTS is a tuple
+%\noteSB{It's a bit strange that algebra presentations are not referred to here}
+Given a term algebra $\Talg$, a pLTS is a tuple
 $pLTS\triangleq\mylangle S,s_0, \to\myrangle$ where:
@@
 $\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in J}\rangle$,
-where $\alpha \in\AlgA$ is a parameterized action, \noteSB{Shouldn't this be $e_b \in \AlgB_{\mathcal{P}}$, for {\em some} $\mathcal{P}$?}\hl{$e_b \in
-\AlgB$} is a guard, and the variables $x_j\in P$
-are assigned the expressions $e_j\in \AlgE$.
+  where $\alpha \in\AlgA_{\P}$ is a parameterized action,
+    $e_b \in \AlgB_{\P}$ is a guard, and the
+  variables $x_j\in P$ are assigned the expressions \noteEM{Or rather
+    $\AlgE_{\P}\cup\AlgA_{P}$ ?}$e_j\in \AlgE_{\P}$. 
 If 
@@
 		J}\rangle} s'\in \to $ then 
-		$\vars(\alpha)\!\subseteq\! \vars(s)$, 
-		\noteSB{I would expect $\vars(e_b)\!\subseteq\! \vars(s)$, since the guard has to be tested on the source state}\hl{$\vars(e_b)\!\subseteq\! \vars(s')$}, and
+%		$\vars(\alpha)\!\subseteq\! \vars(s)$, 
+%		\noteSB{I would expect $\vars(e_b)\!\subseteq\!
+%                  \vars(s)$, since the guard has to be tested on the
+%                 source state}
+%                \hl{$\vars(e_b)\!\subseteq\! \vars(s')$}, and
+                $\vars(e_b)\!\subseteq\! \vars(s)\cup\vars(\alpha)$, and
 		$\forall j\!\in\! J .\,\vars(e_j)\!\subseteq\! \vars(s)\land 
@@
 %\item[$\bullet$]
-The $x_j$ are \emph{state variables} of %% the state
-$s'$. 
+%The $x_j$ are \emph{state variables} of %% the state $s'$. 
 \end{itemize}
@@
 \begin{itemize}
-\item[$\bullet$] \noteSB{Why is one $\I$ and the other $\I_\P$?}\hl{$I \in \I$ and $J\in\I_\P$} are the sets over which are indexed sub-pNets and holes, respectively, such that: $I\cap J=\emptyset$ and  $I\cup J\neq\emptyset$.
+\item[$\bullet$] \noteEM{Pire que ca, $\I$ n'est pas defini...}\noteSB{Why is one $\I$ and the other $\I_\P$?}\hl{$I \in \I$ and $J\in\I_\P$} are the sets over which are indexed sub-pNets and holes, respectively, such that: $I\cap J=\emptyset$ and  $I\cup J\neq\emptyset$.
 
@@
   $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
-  $\forall i\!\in\! I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$\noteSB{What is the sort of a pNet? Should we define $\Sort(\pNet) \triangleq \{\Label(\symb{SV}_k\,|\,k \in K\}$?}, 
+  $\forall i\!\in\! I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$
+%  \noteSB{What is the sort of a pNet? Should we define $\Sort(\pNet)
+%    \triangleq \{\Label(\symb{SV}_k\,|\,k \in K\}$?}
+  , 
   $\forall j\!\in\!
@@
 is an automaton where each transition composes transitions 
-of several \noteSB{These should all be pLTSs, right? Or did I miss something?}\hl{LTSs} with the
+of several \noteSB{These should all be pLTSs, right? Or did I miss
+  something?}\noteEM{Hum, nor really, something intermediate; the actions there can be
+  parameterised actions, but the label has no guard and no assignments}\hl{LTSs} with the
 actions of some holes; the transition occurs if some predicates hold,
@@
 \begin{definition}
-  Given an algebra presentation $\mathcal{P}_{pnet}=<Sorts,Constrs,Ops>$ and a pNet $pnet$, we
+  Given an algebra presentation $\APres_{pnet}=<Sorts,Constrs,Ops>$ and a pNet $pnet$, we
   construct:

### 2018-01-22 2017-Xudong-SMT/FM-2018-extended.tex
section 4

@@
 open automaton semantics. This automaton may then be used to prove
-behavioral properties, like e.g., \TODO{ par exemple ..}
-
+behavioral properties; we give 2 examples, a safety and a liveness
+properties of a BIP architecture.
 \end{abstract}
@@
 is an automaton where each transition composes transitions 
-of several \noteSB{These should all be pLTSs, right? Or did I miss
-  something?}\noteEM{Hum, nor really, something intermediate; the actions there can be
-  parameterised actions, but the label has no guard and no assignments}\hl{LTSs} with the
-actions of some holes; the transition occurs if some predicates hold,
+of several
+% \noteSB{These should all be pLTSs, right? Or did I miss
+%  something?}\noteEM{Hum, nor really, something intermediate; the actions there can be
+%  parameterised actions, but the label has no guard and no
+%  assignments}
+LTSs with the actions of some holes; the transition occurs if some predicates hold,
 and can involve a set of state modifications. Each state of an open
 automaton has a set of \emph{state variables} that can be assigned by
-incoming transitions.
+incoming transitions. Strictly speaking, the LTSs at the leaves of the
+open automaton are a restricted form of pLTSs, where labels are
+parametrised actions, but include no guard nor assignments.
 
@@
 	An \emph{open transition} over a set  $\langle S_i,s_{0 i}, \rightarrow_i\rangle^{i\in
-	I}$ of \hl{LTSs}, a
+	I}$ of LTSs, a
 	set $J$ of holes with sorts $Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is a structure of the form:	
@@
         $i\in I$, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the
-	\hl{LTS} $\langle S_i,s_{0 i}, \rightarrow_i\rangle$, and $\xrightarrow{b_j}_j$
+	LTS $\langle S_i,s_{0 i}, \rightarrow_i\rangle$, and $\xrightarrow{b_j}_j$
         is a transition of the hole $j$, for any action $b_j$ in the
@@
 		\item[$\bullet$]  $I$ and $J$ are  sets of indices,
-		\item[$\bullet$]  \noteSB{And one more above}\hl{$LTS_i^{i\in I}$} is a family of \hl{LTSs},
+		\item[$\bullet$]  $LTS_i^{i\in I}$ is a family of LTSs,
 		\item[$\bullet$]  $\mathcal{S}$ is a set of states and $s_0 \in \mathcal{S}$ the initial state,
@@
 
-\noteSB{line 8: $E$ is never updated, so $E = \emptyset$ always;\\
-line 11: Would it not be better to prune unsatisfiable transitions on-the-fly, \ie inside the loop?}
+\noteSB{
+line 11: Would it not be better to prune unsatisfiable transitions
+on-the-fly, \ie inside the loop?}
+\noteEM{Not so easy, it would require a proof... on one side this
+  would implement reachability on the fly; but there is the question
+  of collecting the assignments of the state variables, that are used
+  in the sat check !}
 Algorithm~\ref{alg1} starts with an open pNet, and builds its set of open
@@
 \begin{algorithmic}[1]
-\Require The pNet node P.
-\State Initialize sets $U=\mathit{InitState}(P)$, $E=\emptyset$ for unexplored/explored global states, $L=\emptyset$ for the resulting OTs;
+\Require The pNet pn (cannot be reduce to a hole)
+\State Initialize sets $U=\{\mathit{InitState}(pn)\}$, $E=\emptyset$
+for unexplored/explored global states, $L=\emptyset$ for the resulting OTs;
 \While{!$\mathit{isEmpty}(U)$}
-	\State Choose $S$ in $U$;
+	\State Choose $S$ in $U$; add $S$ in $E$;
 	\State $\mathit{OT} = \mathit{MakeTransitions}(P, S)$;
@@
         \State Let $T$ be the target global state of $\mathit{OT}$
-	\IfThen{($T \not\in U$ \&\& \hl{$T \not\in E$})}{Add $T$ into $U$;}
+	\IfThen{($T \not\in U$ \&\& $T \not\in E$)}{Add $T$ into $U$;}
 	\EndFor
@@
 \State \hl{Prune the open transitions in $L$ using the SMT solver;}
-\State \Return $\mathit{OA}=\mathit{Reachable}(\mathit{InitState}(P),L)$;
+\State \Return $\mathit{OA}=\mathit{Reachable}(\mathit{InitState}(pn),L)$;
 
@@
 the semantic rules following the structure of the pNet.
-\hl{For pLTSs at the leaves, we simply take the pLTS transitions of the
-corresponding local state and build the predicate to generate the
-open transition.}
-On a pNet node we use two methods, combining and
-matching, to generate the predicate of the open transitions in a
-hierarchical manner.
+When applied to a pLTSs at the leaves, we simply take the pLTS transitions of the
+corresponding local state and use the semantic rule (see TR1 in
+Appendix~\ref{appendix:semRules}) to build the OT. 
+When applied to a pNet node we use two methods, combining and
+matching, to generate the open transitions in a hierarchical manner,
+as detailed in algorithm~\ref{}. This method also manages directly the
+holes of the node, so \emph{MakeTransitions} will never be called on a Hole.
+
 %
@@
 
-\noteInSB{Line 2: Tr1 and Tr2 are the semantic rules, right?}
+%\noteInSB{Line 2: Tr1 and Tr2 are the semantic rules, right?}
 
@@
 
-\noteInSB{Line 8: When is $\mathit{Filter}(ot)$ called?}
+%\noteInSB{Line 8: When is $\mathit{Filter}(ot)$ called?}
 
 \begin{algorithm}
-\caption{MakeTransitions()}
+\caption{MakeTransitions() for pNet nodes}
   \label{alg2}
@@
 	\For{each $\mathit{Subnet}$ in $Pn$}
-	~~~ $\setminus \setminus$ Recursively applying \hl{Tr1 or Tr2} on the sub-nodes.
+	~~~ $\setminus \setminus$ Recursively applying the semantic rules on the sub-nodes.
                 \State Store $\mathit{MakeTransitions}(Subnet, S)$ in $l$;
@@
                  \State \hl{$ot = \mathit{Matching}(sv, \overline{\mathit{comb}}, \mathit{hole})$;} % SB: removed the fourth parameter v here
-                 \State Store $ot$ in $L$; ~~~ \hl{$\setminus \setminus$ if $\mathit{Filter}(ot)$ succeeds}
+                 \State Store $ot$ in $L$; ~~~ \hl{$\setminus \setminus$ when $\mathit{Matching}(ot)$ succeeds}
 	\EndFor
@@
 subnets, as all the possible combinations of their open transitions.
-Assume that there is a collection of $n$ subnets.\noteSB{These variables are not used and conflict with the returned set $L$ in Alg.~\ref{alg2}, on one hand, and control states $s_i$ of the subnets, on the other.}\st{
-$L = {s_1, s_2, ...,  s_n}$;} We denote $\overline{ot}_i$ the set of open
+Assume that there is a collection of $n$ subnets.
+%% \noteSB{These variables are not used and conflict with the returned
+%%   set $L$ in Alg.~\ref{alg2}, on one hand, and control states $s_i$ of
+%%   the subnets, on the other.}
+%% \st{$L = {s_1, s_2, ...,  s_n}$;}
+We denote $\overline{ot}_i$ the set of open
 transitions of the $i$-th
@@
 
-\st{Each of these possible filters is more precise than the previous
-ones. But e}Even when unification succeeds, it is still possible that
+%\st{Each of these possible filters is more precise than the previous
+%  ones. But e}
+Even when unification succeeds, it is still possible that
 the resulting predicate would be unsatisfiable, because of some

### 2018-01-22 2017-Xudong-SMT/FM-2018-extended.tex
section4/5

@@
 \newcommand{\noteInSB}[2][inline,color=green!40]{\todo[#1]{{\bf Simon: } {#2}}}
+\newcommand{\noteInEM}[2][inline,color=green!40]{\todo[#1]{{\bf Eric: } {#2}}}
 \newcommand{\todoMargin}[2][color=red!60, size=\tiny]{\todo[#1]{{\bf
       ToDo: } {#2}}}
+\newcommand{\hlEM}[1]{{\sethlcolor{green}\hl{#1}}}
 
@@
 open automaton semantics. This automaton may then be used to prove
-behavioral properties; we give 2 examples, a safety and a liveness
-properties of a BIP architecture.
+behavioral properties; \hlEM{we give 2 examples, a safety and a liveness
+properties of a BIP architecture}.
 \end{abstract}
@@
   is assigned to its initial value \texttt{Max}.
-\noteSB{This is the first mention of the tool\mdash I would move this text much further.}\hl{In fact this OT is displayed in a simplied, human readable form. The
-raw output of the tool is slightly more difficult to read, in
-particular it uses structured names for the fresh variables generated
-by the algorithm, allowing tracability of the result (see
-appendix~\ref{appendix:variables}). A full output of 
-the use-case is provided in appendice~\ref{appendix:fullOutput}.}
+ A full output of 
+the use-case is provided in appendice~\ref{appendix:fullOutput}.
 
@@
 \EndWhile
-\State \hl{Prune the open transitions in $L$ using the SMT solver;}
+\State \hlEM{Prune the unsatisfiable open transitions in $L$ using the SMT solver;}
 \State \Return $\mathit{OA}=\mathit{Reachable}(\mathit{InitState}(pn),L)$;
@@
 matching, to generate the open transitions in a hierarchical manner,
-as detailed in algorithm~\ref{}. This method also manages directly the
+as detailed in algorithm~\ref{alg2}. This method also manages directly the
 holes of the node, so \emph{MakeTransitions} will never be called on a Hole.
 
-%
 Then, at the root of the pNet, the predicate of each OT is translated
@@
 %
-\noteInSB{Algorithm~\ref{alg2}, as presented below is not
-  well-defined: when we reach the leaves, a pLTS does not have any
-  subnets, hence the loop in lines 2--4 is empty and so is the list
-  $l$. $\mathit{Combining}(l)$ is then called on an empty list...}
+%% \noteInSB{Algorithm~\ref{alg2}, as presented below is not
+%%   well-defined: when we reach the leaves, a pLTS does not have any
+%%   subnets, hence the loop in lines 2--4 is empty and so is the list
+%%   $l$. $\mathit{Combining}(l)$ is then called on an empty list...}
 
@@
 
-\noteInSB{Line 6: Nothing in the assignment $\overline{comb} =
-  \mathit{Combining}(l)$ depends on $sv$.  Hence, this should probably
-  be done outside of the loop.}
+%% \noteInSB{Line 6: Nothing in the assignment $\overline{comb} =
+%%   \mathit{Combining}(l)$ depends on $sv$.  Hence, this should probably
+%%   be done outside of the loop.}
 
@@
   $v$ is fresh.)}
+\noteInEM{Done, please check the new version}
 
@@
 \begin{algorithmic}[1]
-\Require a pNet node $Pn$; a global state $S$.
+\Require a pNet node $Pn$ with subnets $\overline{sn}$ and holes $\overline{hole}$; a global state $S$.
 \State Initialize empty list $l$ and set $L$ for sub-transitions/transitions.
-	\For{each $\mathit{Subnet}$ in $Pn$}
+	\For{each $\mathit{Subnet}$ in $\overline{sn}$}
 	~~~ $\setminus \setminus$ Recursively applying the semantic rules on the sub-nodes.
@@
 	\EndFor
-	\For{each $sv \in SV$}
-		\State $\overline{comb} = \mathit{Combining}(l)$;
-                 \State \hl{$ot = \mathit{Matching}(sv, \overline{\mathit{comb}}, \mathit{hole})$;} % SB: removed the fourth parameter v here
+	\State \hlEM{$\overline{comb} = \mathit{Combining}(l)$;}
+	\For{ \hlEM{each $sv \in SV$, for each $comb \in \overline{comb}$ }}
+           \State \hlEM{$ot = \mathit{Matching}(sv, \overline{\mathit{comb}}, \overline{\mathit{hole}})$;} % SB: removed the fourth parameter v here
            \State Store $ot$ in $L$; ~~~ \hl{$\setminus \setminus$ when $\mathit{Matching}(ot)$ succeeds}
@@
 \paragraph{Matching.}
-The next step, for each synchronisation vector, and each possible
+\hlEM{The \emph{Matching} method builds the OTs of a pNet node from those of
+its subnets (see rule Tr2 in Appendix~\ref{appendix:semRules}).
+For each synchronisation vector, and each possible
 combination of behaviour of the subnets as generated by the \emph
-{Combining} method, consists in building the combined predicate
-and the corresponding open transition.
+{Combining} method, it builds the open transition.
+By lack of space, we only detail here the construction of the predicate.}
 \hl{From a synchronization vector
@@
 \begin{multline*}
-  \mathit{Matching}(sv, C, \mathit{Hole}) = 
+  \mathit{MkPred}(sv, C, \overline{\mathit{hole}}) = 
   \\
@@
   \item if some subnet action expression in the vector does not match (by
-    pattern-matching) the corresponding \hl{action in $C$},
+    pattern-matching) the corresponding \hlEM{action expression in $C$},
   \item or if the whole set of active subnet actions in the vector
-    cannot be matched (by unification) with \hl{the tuple $C$}.
+    cannot be matched (by unification) with \hlEM{the corresponding action expressions
+      tuple $C$}.
 \end {itemize}
@@
 \subsection{Management of state variable assignments}
-%The pLTS contains some variables in each of its states (state
-%variables), or just as global states of the pLTS (global variables).
-%Both can be assigned in the pLTS transitions.
-%The algorithm composing assignments from subnets is different from the
-%generation of predicates. 
-%%When applying Tr1, we just keep the
-%%assignments in the Post of the open transition. And when it comes to
-%%Tr2, Post is the union of the assignments propagate from the
-%%subnets. 
-%The assignments provide value of the variables in
-%predicates. There is usually not only one assignment for a state variable as
-%several incoming transitions of a state can perform different
-%assignments on the same variable. The values of the
-%variables are necessary for checking satisfiability of the open
-%transitions together with predicates, miss of them may drop the
-%unsatisfiable results. In order to avoid such mistakes, the algorithm
-%manages the variables together with a list.
-%
-%The list we used contains triples $<v,\ S, \ AssignRH>$ set for each pLTS to record
-%the information of both state and global variables of the pLTS where $v$ is the variable in pLTS, $S$ is its owner state and $AssignRH$ is a list of expressions over other variables in the right hand side of assignments of $v$.
-The $S$ can be $null$ in the record triple, it means the variable is global in the pLTS belonging to all the states.
-%%So it should be noted that the changing of the value of the global state variable every time a transition is conducted.
-$AssignRH$ is the collection of all the possible expressions coming from the the right hand side of assignments.
-It keeps the information of the assignments for each variable.
-%We update the list of record triples every time Tr1 is applied, adding the right side of the assignments into corresponding expression lists.
-So the list keeps the all the assignments in the pLTS.
-Then we can track all the possible value of the variables when computing open transitions.
-%The initial value of the state variable is also seen as an assignment
-%for that variable. We must give a initial value to the global state
-%variable or there will be some problem in the start state. However, we
-%sometimes don't give initial values to the state variables (except the
-%global variables) as their initial values are decided by their first
-%assignments. Checking whether each variable is initialized before
-%being used is a separated problem, that should be done before starting
-%our algorithm.
 
@@
 % ``global variables'', defined in all states of the pLTS.
-For a global state in the open automaton, getting the set of state
+For a global state in the open automaton, the set of state
 variables (which may be used in a transition) %% will simply be
-\hl{is realised by taking
 the union
-of sets of} state variables of the individual pLTS states constituting this
+of sets of state variables of the individual pLTS states constituting this
 global state (variables of different pLTS are distinct).
@@
 vector (SV0 from Fig.~\ref{schema:ArchFailure:pNet}) does not match
-with these actions, \hl{since it expects $\NameTimer.\PortStart$. This mismatch is materialised} %% as shown
+with these actions, \hl{since it expects $\NameTimer.\PortStart$. This
+  mismatch can be seen} %% as shown 
 by the predicate
@@
 show the Z3 code using its SMT-LIB input language.
+\hl{Note that in the previous sections, the OTs were displayed in a
+  simplied, human readable form. The input and output of our tool, and
+  also the generated SMTlib fragments, are
+  slightly more difficult to read, in 
+particular use structured names for the fresh variables generated
+by the algorithm, allowing tracability of the result (see
+appendix~\ref{appendix:variables})}.
 
@@
 predicate to be checked, encoded as a set of assertions.
-Here we display also the proof generated by Z3,
-\noteSB{I am not sure I understand the entire message of this phrase}\hl{though in practice our tool only needs the brute information ``sat''
-or ``unsat''. The result "unsat" in the output is just what we expected.}
+Here we display also the proof generated by Z3;
+%% \noteSB{I am not sure I understand the entire message of this phrase}\hl{though in practice our tool only needs the brute information ``sat''
+%% or ``unsat''.
+The result "unsat" in the output is just what we expected.
 % as appears in the ``unsat'' proof generated by Z3 in which ``\{= ?x66 ?x70\}'' is shown to be false (see Fig. \ref{schema:smt-lib})

### 2018-01-22 2017-Xudong-SMT/FM-2018-extended.tex
all to page 14

@@
 open automaton semantics. This automaton may then be used to prove
-behavioral properties; \hlEM{we give 2 examples, a safety and a liveness
-properties of a BIP architecture}.
+behavioral properties; we give 2 examples, a safety and a liveness
+properties of a BIP architecture.
 \end{abstract}
@@
   where $\alpha \in\AlgA_{\P}$ is a parameterized action,
-    $e_b \in \AlgB_{\P}$ is a guard, and the
-  variables $x_j\in P$ are assigned the expressions \noteEM{Or rather
-    $\AlgE_{\P}\cup\AlgA_{P}$ ?}$e_j\in \AlgE_{\P}$. 
+    $e_b \in \AlgB_{\P}$ is a guard, and
+    expressions  $\AlgE_{\P}\cup\AlgA_{P}$ are assigned to $x_j$.
 If 
@@
 		J}\rangle} s'\in \to $ then 
-%		$\vars(\alpha)\!\subseteq\! \vars(s)$, 
-%		\noteSB{I would expect $\vars(e_b)\!\subseteq\!
-%                  \vars(s)$, since the guard has to be tested on the
-%                 source state}
-%                \hl{$\vars(e_b)\!\subseteq\! \vars(s')$}, and
                 $\vars(e_b)\!\subseteq\! \vars(s)\cup\vars(\alpha)$, and
@@
 \begin{itemize}
-\item[$\bullet$] \noteEM{Pire que ca, $\I$ n'est pas defini...}\noteSB{Why is one $\I$ and the other $\I_\P$?}\hl{$I \in \I$ and $J\in\I_\P$} are the sets over which are indexed sub-pNets and holes, respectively, such that: $I\cap J=\emptyset$ and  $I\cup J\neq\emptyset$.
+\item[$\bullet$] %\noteEM{Pire que ca, $\I$ n'est pas
+                 %defini...}\noteSB{Why is one $\I$ and the other
+  %$\I_\P$?}
+  $I$ and $J$ are the sets over which are indexed sub-pNets and holes, respectively, such that: $I\cap J=\emptyset$ and  $I\cup J\neq\emptyset$.
 
@@
 
-\noteSB{
-line 11: Would it not be better to prune unsatisfiable transitions
-on-the-fly, \ie inside the loop?}
-\noteEM{Not so easy, it would require a proof... on one side this
-  would implement reachability on the fly; but there is the question
-  of collecting the assignments of the state variables, that are used
-  in the sat check !}
+%% \noteSB{
+%% line 11: Would it not be better to prune unsatisfiable transitions
+%% on-the-fly, \ie inside the loop?}
+%% \noteEM{Not so easy, it would require a proof... on one side this
+%%   would implement reachability on the fly; but there is the question
+%%   of collecting the assignments of the state variables, that are used
+%%   in the sat check !}
 Algorithm~\ref{alg1} starts with an open pNet, and builds its set of open
@@
 \EndWhile
-\State \hlEM{Prune the unsatisfiable open transitions in $L$ using the SMT solver;}
+\State Prune the unsatisfiable open transitions in $L$ using the SMT solver;
 \State \Return $\mathit{OA}=\mathit{Reachable}(\mathit{InitState}(pn),L)$;
@@
 
-\noteInSB{Line 7: There are two type mismatches here: $ot$ is an open
+\noteSB{Line 7: There are two type mismatches here: $ot$ is an open
   transition, whereas $\mathit{Matching}$ is a predicate\mdash one
@@
   $v$ is fresh.)}
-\noteInEM{Done, please check the new version}
+\noteEM{Done, please check the new version}
 
@@
 \begin{algorithm}
-\caption{MakeTransitions() for pNet nodes}
+\caption{MakeTransitions() \em{for a pNet node}}
   \label{alg2}
@@
 	\EndFor
-	\State \hlEM{$\overline{comb} = \mathit{Combining}(l)$;}
-	\For{ \hlEM{each $sv \in SV$, for each $comb \in \overline{comb}$ }}
-           \State \hlEM{$ot = \mathit{Matching}(sv, \overline{\mathit{comb}}, \overline{\mathit{hole}})$;} % SB: removed the fourth parameter v here
-           \State Store $ot$ in $L$; ~~~ \hl{$\setminus \setminus$ when $\mathit{Matching}(ot)$ succeeds}
+	\State $\overline{comb} = \mathit{Combining}(l)$;
+	\For{ each $sv \in SV$, for each $comb \in \overline{comb}$ }
+           \State $ot = \mathit{Matching}(sv, \overline{\mathit{comb}}, \overline{\mathit{hole}})$;
+           \State Store $ot$ in $L$; ~~~ $\setminus \setminus$ when $\mathit{Matching}(ot)$ succeeds
 	\EndFor
@@
 cartesian product:  
-$\overline{comb} = (\inactive\cup \overline{ot}_1) \times (\inactive\cup \overline{ot}_2)\times \dots \times (\inactive\cup \overline{ot}_n)$\hl{, where, for each $i \in [1, n]$, $\overline{ot}_i$ is the set of open transitions obtained from the $i$-th subnet in line~3 of the algorithm}.
+$\overline{comb} = (\inactive\cup \overline{ot}_1) \times (\inactive\cup \overline{ot}_2)\times \dots \times (\inactive\cup \overline{ot}_n)$, where, for each $i \in [1, n]$, $\overline{ot}_i$ is the set of open transitions obtained from the $i$-th subnet in line~3 of the algorithm.
 
@@
 \paragraph{Matching.}
-\hlEM{The \emph{Matching} method builds the OTs of a pNet node from those of
+The \emph{Matching} method builds the OTs of a pNet node from those of
 its subnets (see rule Tr2 in Appendix~\ref{appendix:semRules}).
@@
 {Combining} method, it builds the open transition.
-By lack of space, we only detail here the construction of the predicate.}
-\hl{From a synchronization vector
+By lack of space, we only detail here the construction of the predicate.
+From a synchronization vector
 $sv = \left((a'_i)^{i\in I} (b'_j)^{j\in J}\rightarrow v'\right) \in SV$
 and its guard $G_k$; a tuple of open transitions
-$C = ({ot}_i)^{i \in [1,n]} \in \overline{comb}$, such that, for each $i \in [1,n]$, either $ot_i = -$, or the result action of $ot_i$ is $a_i$; the hole behaviors $\mathit{Hole} = (b_j)^{j \in J}$; and a fresh variable $v$, representing the result action of the OT under construction, we build the predicate}
+$C = ({ot}_i)^{i \in [1,n]} \in \overline{comb}$, such that, for each $i \in [1,n]$, either $ot_i = -$, or the result action of $ot_i$ is $a_i$; the hole behaviors $\mathit{Hole} = (b_j)^{j \in J}$; and a fresh variable $v$, representing the result action of the OT under construction, we build the predicate:
 %
@@
 \paragraph{Filtering.}
-There may be several reasons why such a matching would fail:
+While matching a vector with a combination tuple, \emph{Matching}
+tries to filter out some incompatibilities; there may be several
+reasons why the matching would fail: 
 \begin{itemize}
@@
   \item if some subnet action expression in the vector does not match (by
-    pattern-matching) the corresponding \hlEM{action expression in $C$},
+    pattern-matching) the corresponding action expression in $C$,
   \item or if the whole set of active subnet actions in the vector
-    cannot be matched (by unification) with \hlEM{the corresponding action expressions
-      tuple $C$}.
+    cannot be matched (by unification) with the corresponding action expressions
+      on the tuple $C$.
 \end {itemize}
@@
 
+\begin{figure}[h]
+\begin{mathpar}
+    ot = \openrule{\{s1 \xrightarrow{fail(false)} s1, t1 \xrightarrow{resume(true)} t0\}, ~~\{\xrightarrow{hb}\},~~fail(false)=fail(b_1)\\
+    \OTland resume(true)=start(b_2)\OTland hb=fail(b_0)\OTland v=\underline{fail}\OTland b_1=b_2\\
+    \OTland (b_1\lor b_2) \Rightarrow b_0, ~~\{\}}
+    	   {\ostate{s1,t1} \xrightarrow{v} \ostate{s1,t0}}
+  \end{mathpar}
+\caption{\TODO{Xudong revert to the previous example}One of the unsatisfiable open transitions in the Failure Monitor pNet}  \label{schema:unsat-ot}
+\end{figure}
+
 Our matching/filtering strategy builds some transitions where
@@
 unsatisfiable (symbolic) transition would not be incorrect,
-\hl{we choose to minimize the open automaton (\ie its number of
-transitions and states), by checking these predicates} for satisfiability.
+we choose to minimize the open automaton (\ie its number of
+transitions and states), by checking the predicates for satisfiability.
 In Fig.~\ref{schema:unsat-ot}, we show an 
@@
 vector (SV0 from Fig.~\ref{schema:ArchFailure:pNet}) does not match
-with these actions, \hl{since it expects $\NameTimer.\PortStart$. This
-  mismatch can be seen} %% as shown 
-by the predicate
+with these actions, since it expects $\NameTimer.\PortStart$. This
+  mismatch is materialised by the predicate
 fragment ``$\mathit{resume}(\true)=\mathit{start}(b_2)$''.
-
-\begin{figure}[t]
-\begin{mathpar}
-    ot = \openrule{\{s1 \xrightarrow{fail(false)} s1, t1 \xrightarrow{resume(true)} t0\}, ~~\{\xrightarrow{hb}\},~~fail(false)=fail(b_1)\\
-    \OTland resume(true)=start(b_2)\OTland hb=fail(b_0)\OTland v=\underline{fail}\OTland b_1=b_2\\
-    \OTland (b_1\lor b_2) \Rightarrow b_0, ~~\{\}}
-    	   {\ostate{s1,t1} \xrightarrow{v} \ostate{s1,t0}}
-  \end{mathpar}
-\caption{One of the unsatisfiable open transitions in the Failure Monitor pNet}  \label{schema:unsat-ot}
-\end{figure}
 
@@
 the possible state variable assignments in the source state. In this
-section, we describe the translation of the \noteSB{The algebra presentation only appears here for the first time after its definition in Sect.~\ref{section:pnets}}\hl{algebra presentation}, of
+section, we describe the translation of the algebra presentation, of
 assignments, and of the predicates.
@@
 show the Z3 code using its SMT-LIB input language.
-\hl{Note that in the previous sections, the OTs were displayed in a
+Note that in the previous sections, the OTs were displayed in a
   simplied, human readable form. The input and output of our tool, and
@@
 by the algorithm, allowing tracability of the result (see
-appendix~\ref{appendix:variables})}.
+appendix~\ref{appendix:variables}).
 
@@
     \centerline{\includegraphics[width=\linewidth]{XFIG/SMTLIB3}}
-  \caption{The input of the Z3 solver in SMT-LIB language and the output result}  \label{schema:smt-lib}
+  \caption{\TODO{Xudong: revert to the previous example}The input of the Z3 solver in SMT-LIB language and the output result}  \label{schema:smt-lib}
 \end{figure}
@@
 
-\paragraph{Translating assignments into predicate terms.}
-State variable assignments that were collected during the open
-automaton are used when generating the SMTlib asserts (see
-App.~\ref{appendix:translating-assignments}). \noteSB{I am not an expert of Z3 or SMT-LIB, but the clause '\texttt{(= t (- t 1))}' looks very suspicious to me.}\hl{This appears in
-line 10 of Fig.~\ref{schema:smt-lib}, which encodes possible values of
-the variable $t$ of the timer.}
+%% \paragraph{Translating assignments into predicate terms.}
+%% State variable assignments that were collected during the open
+%% automaton are used when generating the SMTlib asserts (see
+%% App.~\ref{appendix:translating-assignments}). \noteSB{I am not an expert of Z3 or SMT-LIB, but the clause '\texttt{(= t (- t 1))}' looks very suspicious to me.}\hl{This appears in
+%% line 10 of Fig.~\ref{schema:smt-lib}, which encodes possible values of
+%% the variable $t$ of the timer.}
 
@@
 
-\begin{figure}[t]
+\begin{figure}[h]
   \centerline{\includegraphics[width=12cm]{XFIG/FailureTimerOA}}

### 2018-01-22 2017-Xudong-SMT/FM-2018-extended.tex
Revert Fig.3 and 4 to previous example.

@@
 \begin{mathpar}
-    ot = \openrule{\{s1 \xrightarrow{fail(false)} s1, t1 \xrightarrow{resume(true)} t0\}, ~~\{\xrightarrow{hb}\},~~fail(false)=fail(b_1)\\
-    \OTland resume(true)=start(b_2)\OTland hb=fail(b_0)\OTland v=\underline{fail}\OTland b_1=b_2\\
+    ot = \openrule{\{s1 \xrightarrow{fail(false)} s1, t0 \xrightarrow{resume(false)} t0\}, ~~\{\xrightarrow{hb}\},~~fail(false)=fail(b_1)\\
+    \OTland resume(false)=start(b_2)\OTland hb=fail(b_0)\OTland v=\underline{fail}\OTland b_1=b_2\\
     \OTland (b_1\lor b_2) \Rightarrow b_0, ~~\{\}}
-    	   {\ostate{s1,t1} \xrightarrow{v} \ostate{s1,t0}}
+    	   {\ostate{s1,t0} \xrightarrow{v} \ostate{s1,t0}}
   \end{mathpar}

### 2018-01-22 2017-Xudong-SMT/FM-2018-extended.tex
Revert the Fig.3 and Fig.4 .
A transition corrected.

@@
 \begin{mathpar}
-    ot = \openrule{\{s1 \xrightarrow{fail(false)} s1, t0 \xrightarrow{resume(false)} t0\}, ~~\{\xrightarrow{hb}\},~~fail(false)=fail(b_1)\\
+    ot = \openrule{\{s0 \xrightarrow{fail(true)} s0, t0 \xrightarrow{resume(false)} t0\}, ~~\{\xrightarrow{hb}\},~~fail(true)=fail(b_1)\\
     \OTland resume(false)=start(b_2)\OTland hb=fail(b_0)\OTland v=\underline{fail}\OTland b_1=b_2\\
     \OTland (b_1\lor b_2) \Rightarrow b_0, ~~\{\}}
-    	   {\ostate{s1,t0} \xrightarrow{v} \ostate{s1,t0}}
+    	   {\ostate{s0,t0} \xrightarrow{v} \ostate{s0,t0}}
   \end{mathpar}

### 2018-01-22 2017-Xudong-SMT/FM-2018-extended.tex
details in pages 1-14

@@
 but it also allows 
-for more general mechanisms, like gate negotiation in Lotos~\hl{\cite{lotos}}, or broadcast
+for more general mechanisms, like gate negotiation in Lotos~\cite{LotosISO89}, or broadcast
 communications.
@@
   \end{mathpar}
-\caption{\TODO{Xudong revert to the previous example}One of the unsatisfiable open transitions in the Failure Monitor pNet}  \label{schema:unsat-ot}
+\caption{One of the unsatisfiable open transitions in the Failure Monitor pNet}  \label{schema:unsat-ot}
 \end{figure}
@@
   mismatch is materialised by the predicate
-fragment ``$\mathit{resume}(\true)=\mathit{start}(b_2)$''.
+fragment ``$\mathit{resume}(\false)=\mathit{start}(b_2)$''.
 
@@
 
-\begin{figure}[t]
+\begin{figure}[h]
   %  \centerline{\includegraphics[width=12cm]{XFIG/SMTLIB2}}
     \centerline{\includegraphics[width=\linewidth]{XFIG/SMTLIB3}}
-  \caption{\TODO{Xudong: revert to the previous example}The input of the Z3 solver in SMT-LIB language and the output result}  \label{schema:smt-lib}
+  \caption{The input of the Z3 solver in SMT-LIB language and the output result}  \label{schema:smt-lib}
 \end{figure}

### 2018-01-22 2017-Xudong-SMT/FM-2018-extended.tex
Some edits and shortening

@@
 \begin{algorithmic}[1]
-\Require The pNet pn (cannot be reduce to a hole)
-\State Initialize sets $U=\{\mathit{InitState}(pn)\}$, $E=\emptyset$
-for unexplored/explored global states, $L=\emptyset$ for the resulting OTs;
+\Require The pNet \hl{$P$} (cannot be a hole)
+        \qquad \hl{\textbackslash\textbackslash~SB: was `` pn ''}
+\State Initialize sets $U=\{\mathit{InitState}(pn)\}$ and $E=\emptyset$,
+for unexplored and explored global states, respectively; $L=\emptyset$ for the resulting OTs;
 \While{!$\mathit{isEmpty}(U)$}
-	\State Choose $S$ in $U$; add $S$ in $E$;
+	\State Choose $S$ in \hl{$U\setminus E$}; add $S$ in $E$;
+        \qquad \hl{\textbackslash\textbackslash~SB: was `` Choose $S$ in $U$ ''}
 	\State $\mathit{OT} = \mathit{MakeTransitions}(P, S)$;
         \State Store $\mathit{OT}$ in $L$; 
-	\ForAll{$\mathit{OT} \in L$}
+	\For {each $\mathit{OT} \in L$}
         \State Let $T$ be the target global state of $\mathit{OT}$
@@
 corresponding local state and use the semantic rule (see TR1 in
-Appendix~\ref{appendix:semRules}) to build the OT. 
+App.~\ref{appendix:semRules}) to build the OT.\footnote{%
+%
+  \hl{We omit detailed presentation of this case for the sake of brevity.}
+%
+}
 When applied to a pNet node we use two methods, combining and
 matching, to generate the open transitions in a hierarchical manner,
-as detailed in algorithm~\ref{alg2}. This method also manages directly the
-holes of the node, so \emph{MakeTransitions} will never be called on a Hole.
-
-Then, at the root of the pNet, the predicate of each OT is translated
-into SMTlib assertions, and checked for satisfiability. Unsatisfiable
-OTs are pruned, and the final open automaton is computed as the set of
-global states reachable by satisfiable OTs.
+as shown in Alg.~\ref{alg2}. This method directly manages the
+holes of the node, so \emph{MakeTransitions} is never called on a hole.
+
+At the root of the pNet, the predicate of each OT is translated
+into SMTlib assertions, and checked for satisfiability.
+%
+The final open automaton is computed as the set of global states,
+reachable after pruning the unsatisfiable OTs.
+%
+%% Unsatisfiable
+%% OTs are pruned, and the final open automaton is computed as the set of
+%% global states reachable by satisfiable OTs.
 
@@
 
-\noteSB{Line 7: There are two type mismatches here: $ot$ is an open
-  transition, whereas $\mathit{Matching}$ is a predicate\mdash one
-  cannot assign a predicate to an open transition.  Furthermore, in
-  the definition of $\mathit{Matching}$, below, $C_n$ is an open
-  transition, whereas $\overline{comb}$ is a {\em set} of open
-  transitions, so this call does not type either. There is probably
-  another inner loop over all tuples of OTs in $\overline{comb}$; even
-  so the open transition has to be defined completely, not just the
-  predicate\mdash what is the value of $Post$ for the new transition?
-  Maybe $\mathit{Matching}$ should not be a predicate, but an OT?
-  Finally, how is $\mathit{hole}$? (I have removed $v$\mdash here and
-  in the parameters of the definition of the $\mathit{Matching}$
-  predicate, because the text in the paragraph ``Matching'' says that
-  $v$ is fresh.)}
-\noteEM{Done, please check the new version}
+%% \noteSB{Line 7: There are two type mismatches here: $ot$ is an open
+%%   transition, whereas $\mathit{Matching}$ is a predicate\mdash one
+%%   cannot assign a predicate to an open transition.  Furthermore, in
+%%   the definition of $\mathit{Matching}$, below, $C_n$ is an open
+%%   transition, whereas $\overline{comb}$ is a {\em set} of open
+%%   transitions, so this call does not type either. There is probably
+%%   another inner loop over all tuples of OTs in $\overline{comb}$; even
+%%   so the open transition has to be defined completely, not just the
+%%   predicate\mdash what is the value of $Post$ for the new transition?
+%%   Maybe $\mathit{Matching}$ should not be a predicate, but an OT?
+%%   Finally, how is $\mathit{hole}$? (I have removed $v$\mdash here and
+%%   in the parameters of the definition of the $\mathit{Matching}$
+%%   predicate, because the text in the paragraph ``Matching'' says that
+%%   $v$ is fresh.)}
+%% \noteEM{Done, please check the new version}
 
@@
 \begin{algorithmic}[1]
-\Require a pNet node $Pn$ with subnets $\overline{sn}$ and holes $\overline{hole}$; a global state $S$.
-\State Initialize empty list $l$ and set $L$ for sub-transitions/transitions.
+\Require a pNet node $P$ with subnets $\overline{sn}$ and holes $\overline{hole}$; a global state $S$.
+\State Initialize empty list $l$ and set $L$ for sub-transitions and transitions, respectively;
 	\For{each $\mathit{Subnet}$ in $\overline{sn}$}
-	~~~ $\setminus \setminus$ Recursively applying the semantic rules on the sub-nodes.
+        \hfill $\setminus \setminus$ Recursively apply the semantic rules on the subnets
            \State Store $\mathit{MakeTransitions}(Subnet, S)$ in $l$;
@@
 	\State $\overline{comb} = \mathit{Combining}(l)$;
-	\For{ each $sv \in SV$, for each $comb \in \overline{comb}$ }
+	\For{ each $sv \in SV$ and each $comb \in \overline{comb}$ }
            \State $ot = \mathit{Matching}(sv, \overline{\mathit{comb}}, \overline{\mathit{hole}})$;
-           \State Store $ot$ in $L$; ~~~ $\setminus \setminus$ when $\mathit{Matching}(ot)$ succeeds
+           \IfThen{($ot$ is defined)}{Store $ot$ in $L$; ~~~ $\setminus \setminus$ if $\mathit{Matching}()$ succeeds}
 	\EndFor
@@
 The combining method enumerates all the possible behaviours of the
-subnets, as all the possible combinations of their open transitions.
+subnets as all the possible combinations of their open transitions.
 Assume that there is a collection of $n$ subnets.
@@
 transitions of the $i$-th
-subnet; %% $s_i$ and 
+subnet (obtained in line~3 of the algorithm); %% $s_i$ and 
 ``$-$'' means that the subnet is not involved.
@@
 cartesian product:  
-$\overline{comb} = (\inactive\cup \overline{ot}_1) \times (\inactive\cup \overline{ot}_2)\times \dots \times (\inactive\cup \overline{ot}_n)$, where, for each $i \in [1, n]$, $\overline{ot}_i$ is the set of open transitions obtained from the $i$-th subnet in line~3 of the algorithm.
+$\overline{comb} = (\inactive\cup \overline{ot}_1) \times (\inactive\cup \overline{ot}_2)\times \dots \times (\inactive\cup \overline{ot}_n)$.
 
@@
 The \emph{Matching} method builds the OTs of a pNet node from those of
-its subnets (see rule Tr2 in Appendix~\ref{appendix:semRules}).
-For each synchronisation vector, and each possible
-combination of behaviour of the subnets as generated by the \emph
-{Combining} method, it builds the open transition.
-By lack of space, we only detail here the construction of the predicate.
+its subnets (see rule Tr2 in App.~\ref{appendix:semRules}).
+For each synchronisation vector and each possible
+combination of behaviours of the subnets, as generated by the \emph
+{Combining} method, it builds the corresponding open transition.
+Here, we only detail the construction of the predicate.
 From a synchronization vector
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
 \begin{mathpar}
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
   \centerline{\includegraphics[width=12cm]{XFIG/FailureTimerOA}}
@@
 compute all the possible open transitions.
-\hl{The algorithm combines the actions of subnets and
+The algorithm combines the actions of subnets and
 hole behaviors, which are then matched with the
 synchronization vectors by the generated
-predicate.}  Some of the open transitions obtained at this
+predicate.  Some of the open transitions obtained at this
 intermediate step, constructed in a structural manner from all

### 2018-01-22 2017-Xudong-SMT/FM-2018-extended.tex
Added some text in the conclusion about BIP architectures

@@
 Z3 solver. We implemented our algorithm in the VerCors platform and 
-tested the algorithm on available examples, such as encoding expressions from various process algebras. Our case-studies show that our encoding
-successfully identifies all unsatisfiable open transitions and that
+\noteSB{Is this still relevant or has it been replaced by the Failure Monitor example?}%
+\hl{tested the algorithm on available examples, such as encoding expressions from various process algebras}.
+%
+\noteSB{New text}%
+%
+\hl{%
+%
+In this paper, we used an additional running example, based on a BIP
+architecture from an earlier nanosatellite case
+study~\cite{CubETH-case-study}.  This example shows that
+open-automata-based semantics can be instrumental in verifying the
+properties enforced by the architectures through an encoding into open
+pNets.  This encoding\mdash which we intend to formalise and prove
+correct in a separate paper\mdash also opens the way for an extension
+of BIP architectures with the transfer of data among variables of
+different components.  Indeed, such data transfer can be easily
+encoded using the predicates associated to synchronisation vectors in
+open pNets.  The encoding of open transitions into SMTlib and the
+availability of theories can guide the definition of such an extension.
+%
+}
+%
+Our case-studies show that our encoding
+successfully identifies \noteSB{Is this, indeed, the case?}\hl{all} unsatisfiable open transitions and that
 the resulting automata correctly reflect the expected 

### 2018-01-22 2017-Xudong-SMT/FM-2018-extended.tex
Minor edit: moved Fig.4 to the top of the page
Gained 5 lines...

--- 2018-01-22 2017-Xudong-SMT/FM-2018-extended.tex
@@
 \begin{abstract}
-Open pNets are used to model the behavior of open systems, both
+Open pNets are used to model the behaviour of open systems, both
 synchronous or asynchronous, expressed in various calculi or
@@
 open automaton semantics. This automaton may then be used to prove
-behavioral properties; we give 2 examples, a safety and a liveness
+behavioural properties; we give 2 examples, a safety and a liveness
 properties of a BIP architecture.
@@
 In the nineties, several 
-works extended the basic behavioral models based on labelled
+works extended the basic behavioural models based on labelled
 transition systems to address value-passing or parameterized systems, using
@@
 In \cite{Linconcur96}, H.M. Lin addressed value-passing calculi, for which he
-developed a symbolic behavioral semantics, and proved algebraic properties.
+developed a symbolic behavioural semantics, and proved algebraic properties.
 Separately J. Rathke~\cite{HennessyRathke:TCS98} defined another
@@
 Parameterized Networks of Synchronized Automata (pNets) were proposed
-to give a behavioral specification formalism for distributed
-systems, synchronous, asynchronous, or heterogeneous. It is used in
+to give a behavioural specification formalism for distributed
+systems, synchronous, asynchronous, or heterogeneous. They are used in
 VerCors, a platform for designing and 
@@
 high-level languages. The high-level languages in VerCors formalize
-each component of the 
-distributed system and gives out the composition of these
-components.
+each component of the distributed system and their composition.
 pNets provides the core low-level semantic formalism for VerCors, and
@@
 or open expressions of process calculi.
-The open pNet is proposed to solve the
-problem of the undefined components contained in the systems using
-"holes" as the process parameter dealing with these components. The
-hole acts as the placeholder for the uncertain component with a set of
-possible behaviors the component might conduct, presenting the "open"
-property.  
+The open pNet model addresses this problem, using
+"holes" as process parameters, representing \emph{unspecified} subsystems.
 The pNet model was developed in a series of
@@
 Open Automaton in which Open Transitions contain logical predicates
-expressing the relations between the behavior of the holes, and the
-global behavior of the system. In the previous publication,
+expressing the relations between the behaviour of the holes, and the
+global behaviour of the system. In the previous publication,
 only a sketch of a procedure allowing to compute this semantics was
@@
     with their specific decision theories,
-  \item to separate clearly on one hand the algorithmic part, as an
+  \item to separate clearly the 
       algorithm generating the transitions of the open automaton from
-      combination of all possible (symbolic) behaviors; on the other hand
+      combination of all possible (symbolic) behaviours, from
       the symbolic reasoning part, specifically here using an SMT
@@
 process calculi such as CCS and CSP, but communicating by broadcasting
-values, one-to-many communication instead of one-to-one communication
-and transmitting values without blocking. That makes the definition of
+values, %one-to-many communication instead of one-to-one communication and
+transmitting values without blocking. That makes the definition of
 the symbolic semantic and bisimulation equivalence different from the
@@
 
-For other applications, e.g. for the analyses of 
-programming languages, there exist dedicated platforms making use of
+For other applications, such as the analysis of 
+programming languages, there exist dedicated platforms using
 external automatic theorem 
-provers (ATP), or even some automatic tactics from interactive theorem
+provers (ATP) or automatic tactics from interactive theorem
 provers (ITP), to perform symbolic reasoning, and for example to
@@
 already integrated several provers, like Z3, as modules for proving
-the proof obligations generated from the model provided by the user. 
-The prover we used, which also happens to be Z3, is developed by Microsoft Research
+the proof obligations generated from a user model. 
+The prover we use, which also happens to be Z3, is developed by Microsoft Research
 based on the satisfiability modulo 
-theories (SMT), mainly applied in extended static checking, test case
+theories (SMT), is mainly applied in extended static checking, test case
 generation, and predicate abstraction.
 In a similar way, there are several ATPs/ITPs we could consider to use for
-the result pruning and bisimulation checking in our algorithm, as an
+result pruning and bisimulation checking in our algorithm, as an
 alternative to Z3, such as CVC4~\cite{barrett:CAV2011},
@@
 the pNet model, as found in previous publications. Then in section
-\ref{section:examples} we present our use-case, based on an
-industrial-inspired study of the control software of nano-satellites,
-specified using the BIP language. 
+\ref{section:examples} we present our use-case, based on a BIP
+architecture from the nano-satellite case-study. 
 Section \ref{section:op-semantics} recalls briefly the operational semantics
@@
 \emph{parameterized labelled transition systems (pLTSs)}, expressing the
-behavior of basic processes, or \emph{holes}, used as placeholders
+behaviour of basic processes, or \emph{holes}, used as placeholders
 for unknown processes, of which we only specify their set of possible
@@
 symbolic expressions using data types and variables. As we want to encode
-the low-level behavior of possibly very different
+the low-level behaviour of possibly very different
 programming languages, we do not want to impose one specific algebra
@@
   \begin{itemize}
-  \item $Sorts$ is a set of \emph{sorts}\noteSB{Commented out a footnote here\mdash check if still necessary.}
+  \item $Sorts$ is a set of \emph{sorts}
+    % \noteSB{Commented out a footnote here\mdash check if still necessary.}
     %% \footnote{Later we may want to extend this with Sort constructors,
@@
 %  \noteSB{I think this can be removed}\hl{All sorts and operator names must be distinct.}
-  Among constructors, those of arity 0 are called \emph{constants}:
-  $\mathit{Consts}(\APres) = \{\mathit{Con} \in \mathit{Constrs}\,|\, \mathit{arity}(\mathit{Con})=0\}$.
+  Constructors of arity 0 are called \emph{constants}, and denoted $\mathit{Consts}(\APres)$.
+%  $\mathit{Consts}(\APres) = \{\mathit{Con} \in \mathit{Constrs}\,|\, \mathit{arity}(\mathit{Con})=0\}$.
 \end{definition}
@@
 \item[$\bullet$]
-$S$ is a set of \emph{states}.
-\item[$\bullet$]
-$s_0 \in S$ is the \emph{initial state}.
+$S$ is a set of \emph{states}, with $s_0 \in S$ the \emph{initial state}.
 \item[$\bullet$] $\to \subseteq S \times L \times S$ is the \emph{transition relation}, with
@@
 Now, we define
-pNet nodes as constructors for hierarchical behavioral structures.
+pNet nodes as constructors for hierarchical behavioural structures.
 A pNet node has a set of sub-pNets that can be either pNets or pLTSs, and a
@@
 %The open transition $ot_2$ involves the possible actions from the process $P$ and prefix expression $acc(x);Q$.
-The hole behavior, represented by variable $hb_{12}$ must be equal to the exit action $\delta(x)$, and the accept event $acc(x)$ will capture the same value $x$.
+The hole behaviour, represented by variable $hb_{12}$ must be equal to the exit action $\delta(x)$, and the accept event $acc(x)$ will capture the same value $x$.
 %
@@
 
-\begin{algorithm}
+\begin{algorithm}[h]
 \caption{MakeTransitions() \em{for a pNet node}}
@@
 %
-%For holes, their behavior is unspecified, it doesn't have an exact
+%For holes, their behaviour is unspecified, it doesn't have an exact
 %external presentation of action. We only give an action variable to each hole
-%and treat it as hole behavior to suppose working status of the
+%and treat it as hole behaviour to suppose working status of the
 %hole.
 %% Here should have a constraint that this variable belongs to the sort of hole.
-%In every case, the hole behaviors are unchanged, so we
+%In every case, the hole behaviours are unchanged, so we
 %only make the combinations of subnets' open transitions. 
@@
 and its guard $G_k$; a tuple of open transitions
-$C = ({ot}_i)^{i \in [1,n]} \in \overline{comb}$, such that, for each $i \in [1,n]$, either $ot_i = -$, or the result action of $ot_i$ is $a_i$; the hole behaviors $\mathit{Hole} = (b_j)^{j \in J}$; and a fresh variable $v$, representing the result action of the OT under construction, we build the predicate:
+$C = ({ot}_i)^{i \in [1,n]} \in \overline{comb}$, such that, for each $i \in [1,n]$, either $ot_i = -$, or the result action of $ot_i$ is $a_i$; the hole behaviours $\mathit{Hole} = (b_j)^{j \in J}$; and a fresh variable $v$, representing the result action of the OT under construction, we build the predicate:
 %
@@
 \hl{The algorithm combines the actions of subnets and
-hole behaviors, which are then matched with the
+hole behaviours, which are then matched with the
 synchronization vectors by the generated
@@
      variable. Current kinds are: sva\_<SV> (action variable in vector
-     $SV$), ra (result action), hb\_<B> (behavior of hole $B$).
+     $SV$), ra (result action), hb\_<B> (behaviour of hole $B$).
    \item[$\bullet$] $tree\ index$ is the index of the node containing
@@
   rule Tr2, during the construction of each open transition $ot$:
-  Action variables for the behavior of holes and the 
+  Action variables for the behaviour of holes and the 
   resulting actions of transitions, variables created during the cloning
@@
 %    \item (2) The chosen synchronization vector: If the result is also one of the elements, it is also the intermediate variable. Otherwise, all of the parameters are ground.
-%    \item (3) Hole behaviors: Ground.
+%    \item (3) Hole behaviours: Ground.
 %    \item (4) The result action: Not sure. But it must be ground if it is on the root node.
@@
 The substitution will only occur on the argument.
-Actually, what happened is similar if there is a hole behavior instead of a subnet result action attending in the equation.
+Actually, what happened is similar if there is a hole behaviour instead of a subnet result action attending in the equation.
 So we get RL-4 and RL-5.
-However, every hole behavior should be kept through out the computing.
-That's why there no rule similar to the RL-1 for hole behaviors.
+However, every hole behaviour should be kept through out the computing.
+That's why there no rule similar to the RL-1 for hole behaviours.
 }

### 2018-01-22 2017-Xudong-SMT/FM-2018-extended.tex

@@
 
-\begin{figure}[h]
+\begin{figure}[t]
   %  \centerline{\includegraphics[width=12cm]{XFIG/SMTLIB2}}
@@
 compute all the possible open transitions.
-\hl{The algorithm combines the actions of subnets and
-hole behaviours, which are then matched with the
+The algorithm combines the actions of subnets and
+hole behaviors, which are then matched with the
 synchronization vectors by the generated
-predicate.}  Some of the open transitions obtained at this
+predicate.  Some of the open transitions obtained at this
 intermediate step, constructed in a structural manner from all

### 2018-01-22 2017-Xudong-SMT/FM-2018-extended.tex
Scale Up Example.

--- 2018-01-22 2017-Xudong-SMT/FM-2018-extended.tex
@@
 
+\subsection{Scaling up: several subsystems on the same bus}
+\TODO{Not yet !}
+\begin{figure}
+    \centerline{\includegraphics[width=\linewidth]{XFIG/ScaleUp}}
+    \caption{pNet encoding of the composition of two Failure Monitoring modules}  \label{schema:scaleup}
+\end{figure}
+
+We build a larger system by composing several subsystems. In the example here, we use two Failure Monitoring modules as the subsystems.
+To compose them, a new controller is added for managing the reset function of the whole system. 
+No matter which module behaves an "ask" to call for reset, the controller take the request. Then all of the modules conduct the "reset".
+So two more new transitions are added to the Timer to make the module can reset at any state.
+
+There are 327 satisfiable results, out of totally 97920 results, of the example computed in 105384 milliseconds.
+
 \newpage
-\begin{figure}[h]
+\begin{figure}
 $\begin{array}{r@{}l}
@@
 \newpage
-\subsection{Scaling up: several subsystems on the same bus}
-
-\TODO{Not yet !}
-
 \end{document}

### 2018-01-22 2017-Xudong-SMT/FM-2018-extended.tex
perspectives

--- 2018-01-22 2017-Xudong-SMT/FM-2018-extended.tex
@@
 automaton representing the semantics of an open pNet.
-We have also presented our implementation, which comprises two main parts. Firstly, we
-compute all the possible open transitions.
+We have also presented our implementation, which comprises two main
+parts.
+\noteEM{doit pouvoir se reecrire de maniere plus simple et concise...}
+\hl{Firstly, we
+compute} all the possible open transitions.
 The algorithm combines the actions of subnets and
@@
 the predicates before submitting them to the
-Z3 solver. We implemented our algorithm in the VerCors platform and 
-\noteSB{Is this still relevant or has it been replaced by the Failure Monitor example?}%
-\hl{tested the algorithm on available examples, such as encoding expressions from various process algebras}.
-%
-\noteSB{New text}%
-%
-\hl{%
-%
-In this paper, we used an additional running example, based on a BIP
+Z3 solver. 
+%
+%\hl{%
+%
+In this paper, we used a running example, based on a BIP
 architecture from an earlier nanosatellite case
@@
 %
-}
+%}
 %
 Our case-studies show that our encoding
-successfully identifies \noteSB{Is this, indeed, the case?}\hl{all} unsatisfiable open transitions and that
+successfully identifies the unsatisfiable open transitions and that
 the resulting automata correctly reflect the expected 
@@
 
-Among the questions that have arised during this work, an important one is the
-efficiency of Z3 for our needs. Z3 is famous for being very fast in
-solving very large sets of assertions. %% , which could be important for
-%% us
-However, we encountered problems during the implementation of the
-checking method. %% using Z3. 
-For example, if the $\mathit{functions}$ and the
-$\mathit{datatypes}$ part of the algebra presentation that we submit to the solver
-are independent from each other, then checking the $\mathit{assertions}$ is 
-simple. However, $\mathit{functions}$ on recursive $\mathit{datatypes}$ make it
-more complex. Special rules might be defined by the user for the
-induction.  We need more evidence that dealing with more complex
-action algebras, which would involve axiomatizing their data structures
-as Z3 theories, will allow us to decide validity of
-predicates.
-We may also try other automatic theorem provers, depending on the structure of the proofs we need.
-
-\todoMargin{Change perspective: we are working on the formal extension of
-  BIP architectures, and their semantics in terms of pNets. Then
-  bisimulation and model-checking principles adapted to open pNet
-  systems are under development}
+%% Among the questions that have arised during this work, an important one is the
+%% efficiency of Z3 for our needs. Z3 is famous for being very fast in
+%% solving very large sets of assertions. %% , which could be important for
+%% %% us
+%% However, we encountered problems during the implementation of the
+%% checking method. %% using Z3. 
+%% For example, if the $\mathit{functions}$ and the
+%% $\mathit{datatypes}$ part of the algebra presentation that we submit to the solver
+%% are independent from each other, then checking the $\mathit{assertions}$ is 
+%% simple. However, $\mathit{functions}$ on recursive $\mathit{datatypes}$ make it
+%% more complex. Special rules might be defined by the user for the
+%% induction.  We need more evidence that dealing with more complex
+%% action algebras, which would involve axiomatizing their data structures
+%% as Z3 theories, will allow us to decide validity of
+%% predicates.
+%% We may also try other automatic theorem provers, depending on the structure of the proofs we need.
+
+%% \todoMargin{Change perspective: we are working on the formal extension of
+%%   BIP architectures, and their semantics in terms of pNets. Then
+%%   bisimulation and model-checking principles adapted to open pNet
+%%   systems are under development}
 %
 Naturally, our next goals after the generation of the open automata
-will be to model-check, and to check equivalence of  pNets. While
+will be to model-check logical properties, and to check equivalence of pNets. While
 model-checking open automata (with a suitable logic including
@@
 have already found the FH-bisimulation, inspired by~\cite{deSimone85}, to be a
-suitable definition. However, the usual approach of computing bisimulation by partition
-refinement does not work easily with symbolic transitions. In a first
-step we may want instead to define and implement an algorithm for
-checking that a given equivalence relation between open automata 
-states is indeed a FH-Bisimulation. Finding automatically a
-bisimulation relation or the most general bisimulation will be more
-challenging. It appears also that when comparing different pNets with
-different structure, strong bisimulation will be too strong a notion,
-and that we will have to define proper notions of weak equivalence or
-refinements.
+suitable definition. But weak equivalences, or refinements, will
+definitely be useful when comparing different pNets with
+different structure. For bisimulation, we foresee that SMT methods
+will be the basis for comparison of open transitions. 
+%However, the usual approach of computing bisimulation by partition
+%% refinement does not work easily with symbolic transitions. In a first
+%% step we may want instead to define and implement an algorithm for
+%% checking that a given equivalence relation between open automata 
+%% states is indeed a FH-Bisimulation. Finding automatically a
+%% bisimulation relation or the most general bisimulation will be more
+%% challenging.
+%% It appears also that when comparing different pNets with
+%% different structure, strong bisimulation will be too strong a notion,
+%% and that we will have to define proper notions of weak equivalence or
+%% refinements.
+
+\paragraph{Scaling up.} One important motivation of this work is to
+attack the complexity of verification of realistic systems by a
+composition and parametric approach. Still one may wonder if the price
+for analysing our our symbolic transitions will not make the approach
+innaplicable. As a first exercice in this direction, we tried a
+slighly bigger example, assembling 2 Failure controlers. We give some
+figures from this try in appendix~ref{}, showing that Z3 can check the
+satisfiablility of a 90K open transitions in a metter of minutes.
 

### 2018-01-22 2017-Xudong-SMT/FM-2018-extended.tex
pour soumissino temporaire

@@
 
-\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
+%\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
+\newcommand{\TODO}[1]{}
 \newcommand{\NOTE}[1]{\textcolor{blue}{\textbf{[NOTE:#1]}}}
@@
 \begin{algorithmic}[1]
-\Require The pNet \hl{$P$} (cannot be a hole)
-        \qquad \hl{\textbackslash\textbackslash~SB: was `` pn ''}
-\State Initialize sets $U=\{\mathit{InitState}(pn)\}$ and $E=\emptyset$,
+\Require A pNet $P$ (cannot be a hole)
+        %\qquad \hl{\textbackslash\textbackslash~SB: was `` pn ''}
+\State Initialize sets $U=\{\mathit{InitState}(P)\}$ and $E=\emptyset$,
 for unexplored and explored global states, respectively; $L=\emptyset$ for the resulting OTs;
 \While{!$\mathit{isEmpty}(U)$}
-	\State Choose $S$ in \hl{$U\setminus E$}; add $S$ in $E$;
-        \qquad \hl{\textbackslash\textbackslash~SB: was `` Choose $S$ in $U$ ''}
+	\State Choose $S$ in $U\setminus E$; add $S$ in $E$;
+        %\qquad \hl{\textbackslash\textbackslash~SB: was `` Choose $S$ in $U$ ''}
 	\State $\mathit{OT} = \mathit{MakeTransitions}(P, S)$;
@@
 \State Prune the unsatisfiable open transitions in $L$ using the SMT solver;
-\State \Return $\mathit{OA}=\mathit{Reachable}(\mathit{InitState}(pn),L)$;
+\State \Return $\mathit{OA}=\mathit{Reachable}(\mathit{InitState}(P),L)$;
 
@@
 %
-  \hl{We omit detailed presentation of this case for the sake of brevity.}
+  We omit detailed presentation of this case for the sake of brevity.
 %
@@
 parts.
-\noteEM{doit pouvoir se reecrire de maniere plus simple et concise...}
-\hl{Firstly, we
-compute} all the possible open transitions.
+%\noteEM{doit pouvoir se reecrire de maniere plus simple et concise...}
+%\hl{
+  Firstly, we
+  compute
+%}
+all the possible open transitions.
 The algorithm combines the actions of subnets and
@@
 predicates on data) seems easy to define, equivalence checking is more challenging.
-In a previous paper~\hl{\cite{x}}, we
+In~\cite{henrio:Forte2016}, we
 have already found the FH-bisimulation, inspired by~\cite{deSimone85}, to be a
@@
 
-\paragraph{Scaling up.} One important motivation of this work is to
+\emph{Scaling up.} One important motivation of this work is to
 attack the complexity of verification of realistic systems by a

### 2018-01-22 2017-Xudong-SMT/FM-2018-extended.tex
revert TODO
Some modifications in the abstract

@@
 
-%\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
-\newcommand{\TODO}[1]{}
+\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
+%\newcommand{\TODO}[1]{}
 \newcommand{\NOTE}[1]{\textcolor{blue}{\textbf{[NOTE:#1]}}}
@@
 As an industrial oriented use-case, we use so-called "architectures"
-of BIP systems, that have been used to specify the control software of
-ESA microsatellites. We use pNets to encode BIP architectures,
-extended with explicite data in synchronisations, and we compute their
-open automaton semantics. This automaton may then be used to prove
+for BIP systems, that have been used in the framework of an ESA project and to specify the control software of
+a nanosatellite at the EPFL Space Engineering Center. We use pNets to encode a BIP architecture
+extended with explicit data, and compute its
+open automaton semantics. This automaton may be used to prove
 behavioural properties; we give 2 examples, a safety and a liveness
-properties of a BIP architecture.
+property.
 \end{abstract}

### 2018-01-23 2017-Xudong-SMT/FM-2018-extended.tex
partial polish of appendix

@@
 well-formedness of a pNet system, and to define the translation of the pNet
-semantics into the SMT engine input language.
+semantics into the SMT engine input language (\cite{BarFT-RR-17}).
 
@@
 We check the satisfiability of each open transitions
-using the SMT solver Z3. More precisely, we translate
-the OT predicate into an SMTlib assertion in the context provided by
-the possible state variable assignments in the source state. In this
+using the SMT solver Z3.
+%More precisely, we translate
+%the OT predicate into an SMTlib assertion in the context provided by
+%the possible state variable assignments in the source state.
+In this
 section, we describe the translation of the algebra presentation, of
@@
   slightly more difficult to read, in 
-particular use structured names for the fresh variables generated
+particular because of structured names for the fresh variables generated
 by the algorithm, allowing tracability of the result (see
@@
 
+\paragraph{Production of the SMT-lib code}
   To build the input submitted to Z3 for each OT,
 we translate the algebra presentation, the predicates and the
-variable assignments (the Post part) into Z3 (Java-API) syntax.
+variable assignments into Z3 (Java-API) calls.
 % The $presentation$ and the predicates are translated separately.
 
-\paragraph{Translation of action algebra presentation.}
-In App.~\ref{appendix:mapsmt}, we formally define the condition of
+\emph{Translation of action algebra presentation.}
+In Appendix~\ref{appendix:mapsmt}, we  define the condition of
 well-formedness of an algebra presentation, and its translation into
@@
 \texttt{declare-fun}). It ensures that the generated code is correct,
-and will not raise runtime errors in the SMT engine. Remark that the
+and will not raise runtime errors in the SMT engine. Note that the
 \texttt{declare-datatypes} command comprises both the action
@@
 
-\paragraph{Checking satisfiability.}
+\emph{Translation of open transitions}
 
@@
 \begin{itemize}
-\item collect all variables in the transition, and declare them,
+\item collect all variables in the transition, and declare them (using \texttt{declare-const})
 \item check well-formedness and correct typing of expressions,
@@
 The result (sat or unsat) of the final command in the translation (\texttt{check-sat}) is decoded by
-our algorithm.
+)our algorithm.
 
@@
 \item[B] Variable management
+  \subitem B.1 fresh variables
+  \subitem B.2 managment of state variables
 \item[C] Algebra presentations
@@
 \item[E] Translation to SMTlib input language
-\item[F] Full output for our use-case
+\item[F] Full output for the FailureTimer open automaton
+\item[G] Scaling up
 
@@
 \section{Variable management}
+In this section we give more details on two facets of variable
+management in the tool: the generation of variables names, and the
+management of state variable assignments.
+
+\subsection{Fresh variables}
 \label{appendix:variables}
@@
 
-\paragraph{Fresh variables}
 Application of the semantic rules require generating a lot of fresh
@@
 \end{itemize}
+
+\subsection{Management of state variables}
+\label{appendix:translating-assignments}
+In a pLTS, there may be several incoming transitions 
+that assign potentially different values to a state variable.
+To handle such cases, the algorithm manages for each pLTS state, as a
+list of expressions collected from the assignments of each state
+variable $v$ (as registered in the incoming OTs).
+%% The list we used contains triples <$v$, $S$, $AssignRH$> 
+%% where $v$ is the variable in pLTS, $S$ is its owner state and
+%% $AssignRH$ is a list of expressions over other variables in the right
+%% hand side of assignments of $v$.
+% As a pragmatic extension to the formal definition, we also manage
+% ``global variables'', defined in all states of the pLTS.
+For a global state in the open automaton, getting the set of state
+variables (which may be used in a transition) will simply be the union
+of state variables of the individual pLTS states constituting this
+global state, as variables of different pLTS are distinct.
+
+ We define:
+\begin{itemize}
+  \item $SVars(gs)$ the state variables of all states in the global
+    state $gs$
+  \item $Assigns(svar)$ the set of possible assignments of variable
+      $svar$.
+\end{itemize}
+These will be used when translating the predicates into SMTlib
+language.
 
@@
 		&       		\\\specialrule{0em}{5pt}{5pt}
-		(Overloaded FUN)							
+		(Overloaded FUN operator)							
 		&					
@@
 
-\section{Management of state variables}
-\label{appendix:translating-assignments}
-In a pLTS, there may be several incoming transitions 
-that assign potentially different values to a state variable.
-To handle such cases, the algorithm manages for each pLTS state, as a
-list of expressions collected from the assignments of each state
-variable $v$ (as registered in the incoming OTs).
-%% The list we used contains triples <$v$, $S$, $AssignRH$> 
-%% where $v$ is the variable in pLTS, $S$ is its owner state and
-%% $AssignRH$ is a list of expressions over other variables in the right
-%% hand side of assignments of $v$.
-% As a pragmatic extension to the formal definition, we also manage
-% ``global variables'', defined in all states of the pLTS.
-For a global state in the open automaton, getting the set of state
-variables (which may be used in a transition) will simply be the union
-of state variables of the individual pLTS states constituting this
-global state, as variables of different pLTS are distinct.
-
- We define:
-\begin{itemize}
-  \item $SVars(gs)$ the state variables of all states in the global
-    state $gs$
-  \item $Assigns(svar)$ the set of possible assignments of variable
-      $svar$.
-\end{itemize}
-These will be used when translating the predicates into SMTlib
-language.
-
 \section{Translation to SMTlib input language}
@@
 The pNet elements, as defined above, can be full translated into
-SMT-LIB language (\ref{SMTlibv2.5}), but there are a number of differences in the
+SMT-LIB language (\cite{BarFT-RR-17}), but there are a number of differences in the
 structure of the models/languages, so the translation is not trivial.
 
-In this section we shall define separately the translation of the
+In this section we define separately
+\begin{itemize}
+\item The translation of the
 extended algebra presentation for one pNet (so it will be common for
-the study of all OTs of one use-case); and the translation of each
-predicate (of an open-transition) of this pNet.
+the study of all OTs of one use-case);
+\item and the translation of each open transition of the pNet,
+  including its environment (list of variables), its predicate, and
+  the encoding of the possible values of the state-variables of its
+  source global state.
+\end{itemize}
+The following table summarizes the main elements of the translation.
 
@@
 		&$Sorts \& Constructors \translate$	declare-datatypes				\\\specialrule{0em}{1pt}{1pt}
-		&$Operators \lhook\joinrel\longrightarrow$	declare-function		\\\specialrule{0em}{1pt}{1pt}
-		(Predicate)							
+		&$Other operators \lhook\joinrel\longrightarrow$	declare-function		\\\specialrule{0em}{1pt}{1pt}
+		(Open Transition)							
 		&								\\\specialrule{0em}{1pt}{1pt}
@@
 		&$Pred ~~\lhook\joinrel\longrightarrow$	 assert		\\\specialrule{0em}{1pt}{1pt}
-		&$\texttt{FUN}(x_1,...,x_n)$		\\\specialrule{0em}{1pt}{1pt}
+		&$\texttt{FUN}(x_1,...,x_n)$	\TODO {Xudong, why ?}	\\\specialrule{0em}{1pt}{1pt}
 		&$\texttt{pNet expression} ~~\lhook\joinrel\longrightarrow$ SMTLib expression	\\\specialrule{0em}{1pt}{1pt}
-		&$...$	\\\specialrule{0em}{1pt}{1pt}
+		&$assignments$  assert	\\\specialrule{0em}{1pt}{1pt}
 		\specialrule{0em}{1pt}{1pt}\hline
@@
 In the following definitions, we use abstract functions corresponding to
-SMTlib/Z3 constructs. In practice they can be implemented either as
-SMTLib scripting programs, or as calls to the Z3 java API.
-
-\subsubsection{Presentation Translation} \TODO{Duplicate ?}
+SMTlib constructs. In practice they can be implemented either as
+SMTlib scripting programs, or as calls to the Z3 java API.
+
+\subsubsection{Presentation Translation} %\TODO{Duplicate ? no,
+                                %slightly more precise that in the
+                                %paper body.}
 We define here the translation of the algebra presentation, extended
@@
 auxiliary operators as \texttt{declare-function} constructs.
+
 For sorts, we must distinguish the case of mutually defined sorts
 (e.g. edges and vertices in a graph), that must be declared within a
-single \texttt{declare-datatypes} construct. For this we define:
+single \texttt{declare-datatypes} construct. For this we define a
+dependency order on sort, and build the strongly connected components
+of the graph of sorts:
 
 \begin{definition}
-Define the (strict) order "is-using" between sorts $S1 is-using S2$ iff $S2$
+Define the (strict) order "is-using" between sorts $S1~ is-using~ S2$ iff $S2$
 occurs as the sort of one argument in the constructors of $S1$.
@@
   of MySorts with respect to the relation is-using
-- for each SCC in this graph, construct: 
-  datatype-declaration = TrPresentation (Pres, SCC)
-- for each other operator op in Ops, construct:
-  function-declaration = TrPresentation (Pres, op)
+- for each SCC in this graph, construct the definitions, using
+\texttt{declare-datatypes} for sorts, their constants and
+constructors, and \texttt{declare-function} for the other operators,
+using the following translation function:
+
 \end{lstlisting}
@@
 		& 			\\\specialrule{0em}{1pt}{1pt}
-		$\dfrac{n = arity(constr) \neq 0 \qquad |sels|=n
-                  \qquad sels =  BuildSels(constr)}
-                       {constr \translate \texttt{(name($constr$) . sels)}}$
+		$\dfrac{n = arity(constr) \neq 0 \qquad |selectors|=n
+                  \qquad selectors =  BuildSels(constr)}
+                       {constr \translate \texttt{(name($constr$) . $selectors$)}}$
 
@@
 		& 			\\\specialrule{0em}{1pt}{1pt}
-		$\dfrac{op : sort_1, ..., sort_n : sort}
-                       {op \translate \texttt{(declare-fun name($op$) ($sortname_1
-                           ... sortname_n$) $sortname$)}}$
+		$\dfrac{\EPres \vdash op : sort_1, ..., sort_n : sort_0
+                \quad sortname_i = name(sort_i)}
+                {op \translate \texttt{(declare-fun name($op$)
+                    ($sortname_1 ... sortname_n$) $sortname_0$)}}$
 
@@
 		$\dfrac{}
-                       {FUN \translate \texttt{map $\translate CollectFunTypes(pNet)$ }}$
-
-		&&       		\\\specialrule{0em}{1pt}{1pt}
-		$\dfrac{}
-                       {argstypes \translate \texttt{(declare-fun
-                           $BuildFunInstance(argstypes)$ (map name
-                           $argstypes$) Action) }}$
+                       {FUN \translate \texttt{(map $\translate BuildFunInstance(CollectFunTypes(pNet))$) }}$
+
+		%% &&       		\\\specialrule{0em}{1pt}{1pt}
+		%% $\dfrac{}
+                %%        {argstypes \translate
+                %%          \texttt{(declare-fun $BuildFunInstance(argstypes)$}
+                %%          \texttt{(map name $argstypes$) Action) }}$
 
@@
   rules; and $BuildFunInstance$ use these argument types as suffixes
-  to disambiguate 
+  to disambiguate the FUN operator name and build the corresponding
+  \texttt{declare-fun} command.
 \end{itemize}
@@
 \begin{example}
-  For the CCS presentation above, we would get (in SMTLib syntax):
+  For the CCS presentation above\TODO{Check}, we would get:
 \begin{lstlisting}
@@
 
-\TODO{Need to add an example with 2 instances of FUN}
+\begin{example}
+  For our BIP use-case, we have built (see Fig.\ref{schema:smt-lib}):
+  \begin{lstlisting}
+  (declare-datatypes ()
+      ((Action (fail) (resume) (timeout) (reset) (start) (tick) (ask)
+    (FUN_Action_Bool (fst Action) (snd Bool))
+    (Synchro (action Action)))))
+  \end{lstlisting}
+\end{example}
 
@@
 
-\subsection{properties}
+\paragraph{properties}
 The rules in the sections above are meant to guarantee that no runtime
@@
 \label{appendix:fullOutput}
-
+The following listing contains the final list of OTs generated for our
+use-case. It is displayed in full and raw format, each OT containing
+in its premisses: the list of transitions of pLTSs and actions of
+holes, the predicate, the Post assignements. In the conclusion the
+transition labelled by a fresh ``result'' variable.
+
+\newpage
 \begin{lstlisting}[basicstyle=\scriptsize\ttfamily, frame=single]
    {s0---failure(true)-->s1, t0---start(true)-->t1},{---:hb_B:13:1-->},   
-	(failure(true)=failure(b1:sva_SV0:1:1))
-	/\(start(true)=start(b2:sva_SV0:1:1))
+   (failure(true)=failure(b1:sva_SV0:1:1))/\(start(true)=start(b2:sva_SV0:1:1))
    /\(:hb_B:13:1=fail(b0:sva_SV0:1:1))/\((b1:sva_SV0:1:1=b2:sva_SV0:1:1)
@@
    {s1---resume(true)-->s0, t1---resume(true)-->t0},{---:hb_B:16:2-->},   
-	(resume(true)=resume(b1:sva_SV1:1:2))
-	/\(resume(true)=resume(b2:sva_SV1:1:2))
+   (resume(true)=resume(b1:sva_SV1:1:2))/\(resume(true)=resume(b2:sva_SV1:1:2))
    /\(:hb_B:16:2=resume(b0:sva_SV1:1:2))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2)
@@
 
-\subsection{Scaling up: several subsystems on the same bus}
-\TODO{Not yet !}
-\begin{figure}
-    \centerline{\includegraphics[width=\linewidth]{XFIG/ScaleUp}}
-    \caption{pNet encoding of the composition of two Failure Monitoring modules}  \label{schema:scaleup}
-\end{figure}
-
-We build a larger system by composing several subsystems. In the example here, we use two Failure Monitoring modules as the subsystems.
-To compose them, a new controller is added for managing the reset function of the whole system. 
-No matter which module behaves an "ask" to call for reset, the controller take the request. Then all of the modules conduct the "reset".
-So two more new transitions are added to the Timer to make the module can reset at any state.
-
-There are 327 satisfiable results, out of totally 97920 results, of the example computed in 105384 milliseconds.
-
 \newpage
-\begin{figure}
+\begin{figure}[h]
 $\begin{array}{r@{}l}
@@
 \newpage
+\subsection{Scaling up: several subsystems on the same bus}
+
+\begin{figure}
+    \centerline{\includegraphics[width=\linewidth]{XFIG/ScaleUp}}
+    \caption{pNet encoding of the composition of two Failure Monitoring modules}  \label{schema:scaleup}
+\end{figure}
+
+We build a larger system by composing several subsystems. In the example here, we use two Failure Monitoring modules as the subsystems.
+To compose them, a new controller is added for managing the reset function of the whole system. 
+No matter which module behaves an "ask" to call for reset, the controller take the request. Then all of the modules conduct the "reset".
+So two more new transitions are added to the Timer to make the module can reset at any state.
+
+There are 327 satisfiable results, out of totally 97920 results, of the example computed in 105384 milliseconds.
+
 \end{document}

### 2018-01-23 2017-Xudong-SMT/FM-2018-extended.tex
Update the scale up graph.
more appendix

@@
   (\forall i\in I, a_i=a'_i) \land
-  (\forall i \not\in I, ot_i = -) \land
+%  (\forall i \not\in I, ot_i = -) \land
   (\forall j\in J, b_j=b'_j) \land
@@
 incompatibility involving the guards. In our algorithm, we choose to
-apply only the simplest filter inside the \emph{Matching} method. All
+apply only the simplest filter inside the \emph{Matching} method
+(before applying the predicate and OT construction). All
 the rest will be checked later, using the satisfiability check in the
@@
 
-To have some practical interest, it is important to know when this
-algorithm terminates. The following theorem shows that an open-pNet
-with finite synchronization sets, finitely many leaves and
-holes, and each pLTS at leaves having a finite number of states and
-(symbolic) transitions, has a finite automaton. The proof can be found
-in \cite{henrio:Forte2016}.
-
 In rule TR2, the generated predicate is composed of the conjunction of
@@
 
-This definition is not constructive, but the existentialy quantified
-variable sets here correspond the subsets of subnets and holes that
-are effectively involved in vector $SV_k$.
-Within our algorithm, these subsets have been computed by $Combining$ and
-passed as arguments to the $Matching$ method, so
-we can construct this predicate fragment as:
-
-\[\Pred(SV, \overline{\pNet},\overline{S}, v) = 
-\begin{array}{l}
-\forall {(a'_i)}^{i\in I},
-{(b'_j)}^{j\in J},v'.
-\\
-v_m=a'_i\land \, b_j=b'_j \land v=v' \land G_k
-\end{array}\]
-\TODO{Eric: to be checked}
+%% This definition is not constructive, but the existentialy quantified
+%% variable sets here correspond the subsets of subnets and holes that
+%% are effectively involved in vector $SV_k$.
+%% Within our algorithm, these subsets have been computed by $Combining$ and
+%% passed as arguments to the $Matching$ method, so
+%% we can construct this predicate fragment as:
+
+%% \[\Pred(SV, \overline{\pNet},\overline{S}, v) = 
+%% \begin{array}{l}
+%% \forall {(a'_i)}^{i\in I},
+%% {(b'_j)}^{j\in J},v'.
+%% \\
+%% v_m=a'_i\land \, b_j=b'_j \land v=v' \land G_k
+%% \end{array}\]
+%% \TODO{Eric: to be checked}
+
+Within our algorithm, these subsets have been computed by the
+$Combining$ method and passed as arguments to the $Matching$ method
+(see section~\ref{section:implementation})
+
+\paragraph{Termination.} To have some practical interest, it is important to know when this
+algorithm terminates. The following theorem shows that an open-pNet
+with finite synchronization sets, finitely many leaves and
+holes, and each pLTS at leaves having a finite number of states and
+(symbolic) transitions, has a finite automaton. The proof can be found
+in \cite{henrio:Forte2016}.
 
@@
 \begin{example}
+  \label{example:CCSpresentation}
   \begin{itemize}
@@
 \begin{example}
-  For the CCS presentation above\TODO{Check}, we would get:
+  For the CCS presentation in example~\ref{example:CCSpresentation}, we would get:
 \begin{lstlisting}
@@
 
-Each time we submit each open transition to Z3 module, we translate
-  its predicate into the SMTlib language  and send it for satisfiability
-  checking. Every term of the predicate is declared as an
-  \texttt{assert} in Z3. A constant action or a parameterized
-  expression is easy to get from the internal list storing the objects
-  while all the variables are not declared at the beginning. So we
-  declare them before the submission of a predicate term with the API
-  method conducting \texttt{declare-const}.
+%% Each time we submit each open transition to Z3 module, we translate
+%%   its predicate into the SMTlib language  and send it for satisfiability
+%%   checking. Every term of the predicate is declared as an
+%%   \texttt{assert} in Z3. A constant action or a parameterized
+%%   expression is easy to get from the internal list storing the objects
+%%   while all the variables are not declared at the beginning. So we
+%%   declare them before the submission of a predicate term with the API
+%%   method conducting \texttt{declare-const}.
 
@@
 \begin{itemize}
-\item compute the environment $\EEnv=\EEnv_{pnet,OT}$ collecting
+\item[$\bullet$] Environnement and correctness
+  \subitem compute the environment $\EEnv=\EEnv_{pnet,OT}$ collecting
 all variables used in OT.
-\item check that all pLTS labels (action, guard, assignment) in
+\subitem check that all pLTS labels (action, guard, assignment) in
 the transition, the OT predicate, and the OT assignments are
 well-formed and well-typed.
-\item for each start global state $gs$ of the open transition, using $SVar(gs)$
+\subitem for each variable $v$ in $\EEnv$, construct:
+  define-const = TrPredicate ($\EEnv ,v$).
+\item[$\bullet$] Assignments: for each start global state $gs$ of the open transition, using $SVar(gs)$
   get the state variables and their possible evaluations from all the state in $gs$.
   Then use Assigns(x) as the set of evaluations of state variable x.
-\item for each variable $v$ in $\EEnv$, construct:
-  define-const = TrPredicate ($\EEnv ,v$).
 %- turn the predicate into conjunctive normal form
-\item for each conjunct $P_i$ in the predicate, construct:
+\item[$\bullet$] Predicate: Decompose the toplevel conjuncts of the predicate. For each conjunct $P_i$, construct:
   assert = TrPredicate $(P_i)$.
@@
 % \TODO{This is incomplete... Xudong: Conjunctive normal form, translation function for Boolean expressions, + assignments}
-
-\noindent
+\smallskip
+In the following table, we denote $\translate$ the main translation
+function, and $\longrightarrow$ the TrPredicate auxiliary function.
+
+\medskip\noindent
 \begin{tabular}{p{5cm}p{7cm}}
 		\hline\specialrule{0em}{3pt}{3pt}
-		\multicolumn{2}{l}{Variables:}
+		Variables:
 		\\
@@
                        {x \translate \texttt{(declare-const x A)}}$&
-		\\\specialrule{0em}{3pt}{3pt}
+		\\\specialrule{0em}{3pt}{3pt}\hline\specialrule{0em}{3pt}{5pt}
 		Open transition: 
@@
 		$\dfrac{Pred \translate lst_1~~Ass \translate lst_2}{ot(Pred, Ass) \translate lst_1 lst_2}$
+		\\\specialrule{0em}{3pt}{3pt}\hline\specialrule{0em}{3pt}{5pt}
+		Assignment: 
+		\\
+		$\dfrac{Ass = \bigwedge\limits_{k\in K}(x_k, a_k)~~x_k\in SVar(gs)~~a_k = Assigns(x_k)}{Ass \translate \texttt{map} \translate (x_k, a_k)}$
 		\\\specialrule{0em}{3pt}{3pt}		
+		$\dfrac{a_k = e_1,...,e_n}{(x_k, a_k) \translate \texttt{(assert (or (= }x_k\texttt{ map} \longrightarrow e_1\texttt{)}\texttt{...(= }x_k\texttt{ map} \longrightarrow e_n\texttt{)}  \texttt{))}}$
+		\\\specialrule{0em}{3pt}{3pt}\hline\specialrule{0em}{3pt}{5pt}
 		Predicate: & Predicate conjunct:
@@
 		$\dfrac{arg = op'(args)~~op'\in Ops}{op' \longrightarrow \texttt{(}name(op')~~map\longrightarrow args\texttt{)}}$
-		\\\specialrule{0em}{3pt}{3pt}
-		Assignment: 
-		\\
-		$\dfrac{Ass = \bigwedge\limits_{k\in K}(x_k, a_k)~~x_k\in SVar(gs)~~a_k = Assigns(x_k)}{Ass \translate \texttt{map} \translate (x_k, a_k)}$
-		\\\specialrule{0em}{3pt}{3pt}		
-		$\dfrac{a_k = e_1,...,e_n}{(x_k, a_k) \translate \texttt{(assert (or (= }x_k\texttt{ map} \longrightarrow e_1\texttt{)}\texttt{...(= }x_k\texttt{ map} \longrightarrow e_n\texttt{)}  \texttt{))}}$
 		\\\\\specialrule{0em}{1pt}{1pt}

### 2018-01-23 2017-Xudong-SMT/FM-2018-extended.tex
appendix G

@@
 		&$Pred ~~\lhook\joinrel\longrightarrow$	 assert		\\\specialrule{0em}{1pt}{1pt}
-		&$\texttt{FUN}(x_1,...,x_n)$	\TODO {Xudong, why ?}	\\\specialrule{0em}{1pt}{1pt}
+%		&$\texttt{FUN}(x_1,...,x_n)$	\TODO {Xudong, why ?}	\\\specialrule{0em}{1pt}{1pt}
 		&$\texttt{pNet expression} ~~\lhook\joinrel\longrightarrow$ SMTLib expression	\\\specialrule{0em}{1pt}{1pt}
@@
 
+In Fig.~\ref{schema:ots} we display the same OTs in a more human friendly format (but manualy translated into latex).
+
+\begin{figure}[h]
+$\begin{array}{r@{}l}
+    ot_1  = &\openrule{\{s0 \xrightarrow{\OTvar{fail(true)}} s1, t0 \xrightarrow{\OTvar{start(true)}} t1\}, ~~\{\xrightarrow{hb_1}\},~~\OTvar{fail(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
+    \OTland \OTvar{start(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland hb_1=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\\
+    \OTland v_1=\OTvar{\underline{fail}}\OTland \OTvar{b}_1 = \OTvar{b}_2
+    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{t := Max\}}
+           {\ostate{s0,t0} \xrightarrow{v_1} \ostate{s1,t1}}\\
+\end{array}$
+  \smallskip
+
+$\begin{array}{r@{}l}
+    ot_2  = &\openrule{\{s0 \xrightarrow{\OTvar{resume(false)}} s0, t0 \xrightarrow{\OTvar{resume(false)}} t0\}, ~~\{\xrightarrow{hb_2}\},~~\OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_1\OTvar{)}\\
+    \OTland \OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_2=\OTvar{resume(}\OTvar{b}_0\OTvar{)}\\
+    \OTland v_2=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
+    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
+            {\ostate{s0,t0} \xrightarrow{v_2} \ostate{s0,t0}}\\
+  \end{array}$
+\smallskip
+
+$\begin{array}{r@{}l}
+    ot_3  = &\openrule{\{\}, ~~\{\xrightarrow{hb_3}\},~~hb_3=\OTvar{finish}\OTland v_3=\OTvar{finish}, ~~\{\}}
+            {\ostate{s0,t0} \xrightarrow{v_3} \ostate{s0,t0}}\\
+\end{array}$
+\smallskip
+
+$\begin{array}{r@{}l}
+    ot_4  = &\openrule{\{s1 \xrightarrow{\OTvar{fail(false)}} s1, t1 \xrightarrow{\OTvar{start(false)}} t1\}, ~~\{\xrightarrow{hb_4}\},~~\OTvar{fail(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
+    \OTland \OTvar{start(false)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland hb_4=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\\
+    \OTland v_4=\OTvar{\underline{fail}}\OTland \OTvar{b}_1 = \OTvar{b}_2
+    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
+           {\ostate{s1,t1} \xrightarrow{v_4} \ostate{s1,t1}}\\
+\end{array}$
+\smallskip
+
+$\begin{array}{r@{}l}
+    ot_5  = &\openrule{\{s1 \xrightarrow{\OTvar{resume(true)}} s0, t1 \xrightarrow{\OTvar{resume(true)}} t0\}, ~~\{\xrightarrow{hb_5}\},~~\OTvar{resume(true)}=\OTvar{resume(}\OTvar{b}_1\OTvar{)}\\
+    \OTland \OTvar{resume(true)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_2=\OTvar{resume(}\OTvar{b}_0\OTvar{)}\\
+    \OTland v_5=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
+    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
+            {\ostate{s1,t1} \xrightarrow{v_5} \ostate{s0,t0}}\\
+\end{array}$
+\smallskip
+
+$\begin{array}{r@{}l}
+    ot_6  = &\openrule{\{t1 \xrightarrow{\OTvar{tick}} t1\}, ~~\{\},~~t\neq 0\OTland v_6=\OTvar{tick}, ~~\{t := t-1 \}}
+           {\ostate{s1,t1} \xrightarrow{v_6} \ostate{s1,t0}}\\
+\end{array}$
+\smallskip
+
+$\begin{array}{r@{}l}
+    ot_7  = &\openrule{\{\}, ~~\{\xrightarrow{hb_7}\},~~hb_7=\OTvar{finish}\OTland v_7=\OTvar{finish}, ~~\{\}}
+            {\ostate{s1,t1} \xrightarrow{v_7} \ostate{s1,t1}}\\
+\end{array}$
+\smallskip
+
+$\begin{array}{r@{}l}
+    ot_8  = &\openrule{\{s1 \xrightarrow{\OTvar{timeout}} s2, t1 \xrightarrow{\OTvar{timeout}} t0\}, ~~\{\},~~t=0\OTland v_8=ask, ~~\{\}}
+           {\ostate{s1,t1} \xrightarrow{v_8} \ostate{s2,t0}}\\
+\end{array}$
+\smallskip
+
+$\begin{array}{r@{}l}
+    ot_9  = &\openrule{\{s2 \xrightarrow{\OTvar{resume(false)}} s2, t0 \xrightarrow{\OTvar{resume(false)}} t0\}, ~~\{\xrightarrow{hb_9}\},~~\OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_1\OTvar{)}\\
+    \OTland \OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_9=\OTvar{resume(}\OTvar{b}_0\OTvar{)}\\
+    \OTland v_9=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
+    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
+            {\ostate{s2,t0} \xrightarrow{v_9} \ostate{s2,t0}}\\
+\end{array}$
+\smallskip
+
+$\begin{array}{r@{}l}
+    ot_{10}  = &\openrule{\{s2 \xrightarrow{\OTvar{reset}} s0\}, ~~\{\},~~v_{10}=\OTvar{reset}, ~~\{\}}
+           {\ostate{s2,t0} \xrightarrow{v_{10}} \ostate{s0,t0}}\\
+\end{array}$
+\smallskip
+
+$\begin{array}{r@{}l}
+    ot_{11}  = &\openrule{\{\}, ~~\{hb_{11}\},~~hb_{11}=\OTvar{finish}\OTland v_{11}=\OTvar{finish}, ~~\{\}}
+           {\ostate{s2,t0} \xrightarrow{v_{11}} \ostate{s2,t0}}\\
+\end{array}$
+\caption{The open transitions of the open automaton}  \label{schema:ots}
+\end{figure}
+
 \newpage
@@
 \newpage
-\begin{figure}[h]
-$\begin{array}{r@{}l}
-    ot_1  = &\openrule{\{s0 \xrightarrow{\OTvar{fail(true)}} s1, t0 \xrightarrow{\OTvar{start(true)}} t1\}, ~~\{\xrightarrow{hb_1}\},~~\OTvar{fail(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
-    \OTland \OTvar{start(true)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland hb_1=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\\
-    \OTland v_1=\OTvar{\underline{fail}}\OTland \OTvar{b}_1 = \OTvar{b}_2
-    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{t := Max\}}
-           {\ostate{s0,t0} \xrightarrow{v_1} \ostate{s1,t1}}\\
-\end{array}$
-  \smallskip
-
-$\begin{array}{r@{}l}
-    ot_2  = &\openrule{\{s0 \xrightarrow{\OTvar{resume(false)}} s0, t0 \xrightarrow{\OTvar{resume(false)}} t0\}, ~~\{\xrightarrow{hb_2}\},~~\OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_1\OTvar{)}\\
-    \OTland \OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_2=\OTvar{resume(}\OTvar{b}_0\OTvar{)}\\
-    \OTland v_2=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
-    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
-            {\ostate{s0,t0} \xrightarrow{v_2} \ostate{s0,t0}}\\
-  \end{array}$
-\smallskip
-
-$\begin{array}{r@{}l}
-    ot_3  = &\openrule{\{\}, ~~\{\xrightarrow{hb_3}\},~~hb_3=\OTvar{finish}\OTland v_3=\OTvar{finish}, ~~\{\}}
-            {\ostate{s0,t0} \xrightarrow{v_3} \ostate{s0,t0}}\\
-\end{array}$
-\smallskip
-
-$\begin{array}{r@{}l}
-    ot_4  = &\openrule{\{s1 \xrightarrow{\OTvar{fail(false)}} s1, t1 \xrightarrow{\OTvar{start(false)}} t1\}, ~~\{\xrightarrow{hb_4}\},~~\OTvar{fail(false)}=\OTvar{fail(}\OTvar{b}_1\OTvar{)}\\
-    \OTland \OTvar{start(false)}=\OTvar{start(}\OTvar{b}_2\OTvar{)}\OTland hb_4=\OTvar{fail(}\OTvar{b}_0\OTvar{)}\\
-    \OTland v_4=\OTvar{\underline{fail}}\OTland \OTvar{b}_1 = \OTvar{b}_2
-    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
-           {\ostate{s1,t1} \xrightarrow{v_4} \ostate{s1,t1}}\\
-\end{array}$
-\smallskip
-
-$\begin{array}{r@{}l}
-    ot_5  = &\openrule{\{s1 \xrightarrow{\OTvar{resume(true)}} s0, t1 \xrightarrow{\OTvar{resume(true)}} t0\}, ~~\{\xrightarrow{hb_5}\},~~\OTvar{resume(true)}=\OTvar{resume(}\OTvar{b}_1\OTvar{)}\\
-    \OTland \OTvar{resume(true)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_2=\OTvar{resume(}\OTvar{b}_0\OTvar{)}\\
-    \OTland v_5=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
-    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
-            {\ostate{s1,t1} \xrightarrow{v_5} \ostate{s0,t0}}\\
-\end{array}$
-\smallskip
-
-$\begin{array}{r@{}l}
-    ot_6  = &\openrule{\{t1 \xrightarrow{\OTvar{tick}} t1\}, ~~\{\},~~t\neq 0\OTland v_6=\OTvar{tick}, ~~\{t := t-1 \}}
-           {\ostate{s1,t1} \xrightarrow{v_6} \ostate{s1,t0}}\\
-\end{array}$
-\smallskip
-
-$\begin{array}{r@{}l}
-    ot_7  = &\openrule{\{\}, ~~\{\xrightarrow{hb_7}\},~~hb_7=\OTvar{finish}\OTland v_7=\OTvar{finish}, ~~\{\}}
-            {\ostate{s1,t1} \xrightarrow{v_7} \ostate{s1,t1}}\\
-\end{array}$
-\smallskip
-
-$\begin{array}{r@{}l}
-    ot_8  = &\openrule{\{s1 \xrightarrow{\OTvar{timeout}} s2, t1 \xrightarrow{\OTvar{timeout}} t0\}, ~~\{\},~~t=0\OTland v_8=ask, ~~\{\}}
-           {\ostate{s1,t1} \xrightarrow{v_8} \ostate{s2,t0}}\\
-\end{array}$
-\smallskip
-
-$\begin{array}{r@{}l}
-    ot_9  = &\openrule{\{s2 \xrightarrow{\OTvar{resume(false)}} s2, t0 \xrightarrow{\OTvar{resume(false)}} t0\}, ~~\{\xrightarrow{hb_9}\},~~\OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_1\OTvar{)}\\
-    \OTland \OTvar{resume(false)}=\OTvar{resume(}\OTvar{b}_2\OTvar{)}\OTland hb_9=\OTvar{resume(}\OTvar{b}_0\OTvar{)}\\
-    \OTland v_9=\OTvar{\underline{resume}}\OTland \OTvar{b}_1 = \OTvar{b}_2
-    \OTland \OTvar{(}\OTvar{b}_1 \lor \OTvar{b}_2\OTvar{)} \Rightarrow \OTvar{b}_0, ~~\{\}}
-            {\ostate{s2,t0} \xrightarrow{v_9} \ostate{s2,t0}}\\
-\end{array}$
-\smallskip
-
-$\begin{array}{r@{}l}
-    ot_{10}  = &\openrule{\{s2 \xrightarrow{\OTvar{reset}} s0\}, ~~\{\},~~v_{10}=\OTvar{reset}, ~~\{\}}
-           {\ostate{s2,t0} \xrightarrow{v_{10}} \ostate{s0,t0}}\\
-\end{array}$
-\smallskip
-
-$\begin{array}{r@{}l}
-    ot_{11}  = &\openrule{\{\}, ~~\{hb_{11}\},~~hb_{11}=\OTvar{finish}\OTland v_{11}=\OTvar{finish}, ~~\{\}}
-           {\ostate{s2,t0} \xrightarrow{v_{11}} \ostate{s2,t0}}\\
-\end{array}$
-\caption{The open transitions of the open automaton}  \label{schema:ots}
-\end{figure}
-
-\newpage
 \subsection{Scaling up: several subsystems on the same bus}
@@
     \centerline{\includegraphics[width=\linewidth]{XFIG/ScaleUp}}
-    \caption{pNet encoding of the composition of two Failure Monitoring modules}  \label{schema:scaleup}
+    \caption{pNet encoding of the composition of two Failure
+      Monitoring modules}  \label{schema:scaleup} 
 \end{figure}
 
-We build a larger system by composing several subsystems. In the example here, we use two Failure Monitoring modules as the subsystems.
-To compose them, a new controller is added for managing the reset function of the whole system. 
-No matter which module behaves an "ask" to call for reset, the controller take the request. Then all of the modules conduct the "reset".
-So two more new transitions are added to the Timer to make the module can reset at any state.
-
-There are 327 satisfiable results, out of totally 97920 results, of the example computed in 105384 milliseconds.
+We build a larger system by composing several subsystems. In the
+example here (Fig.~\ref{schema:scaleup}), we use two Failure
+Monitoring modules. 
+To compose them, a new controller is added for managing the reset
+function of the whole system.  
+No matter which module emits an "ask" to call for reset, the
+controller take the request. Then all of the modules are synchronised
+on the "reset". 
+So two more new transitions are added to the Timer to ensure the
+module can reset at any state.
+
+There are 327 satisfiable results, out of totally 97920 results, of
+the example computed in 105384 milliseconds (~1.45 minutes).
 

### 2018-01-23 2017-Xudong-SMT/FM-2018-extended.tex
Add running info about scale up example.

@@
 There are 327 satisfiable results, out of totally 97920 results, of
-the example computed in 105384 milliseconds (~1.45 minutes).
-
+the example computed in 105384 milliseconds (~1.45 minutes), 
+which was carried out on an Intel Core i7 at 2.5GHz with 16GB of RAM.
+
+Then we found some extra states that never found when running only the subnets.
+We figured out that is caused by a input mistake easily comparing it with the results on subnets.
 \end{document}

### 2018-01-23 2017-Xudong-SMT/FM-2018-extended.tex
conclusino

--- 2018-01-23 2017-Xudong-SMT/FM-2018-extended.tex
@@
 
-In this paper, we presented an algorithm for generating an open
-automaton representing the semantics of an open pNet.
-We have also presented our implementation, which comprises two main
-parts.
-%\noteEM{doit pouvoir se reecrire de maniere plus simple et concise...}
-%\hl{
-  Firstly, we
-  compute
-%}
-all the possible open transitions.
-The algorithm combines the actions of subnets and
-hole behaviors, which are then matched with the
-synchronization vectors by the generated
-predicate.  Some of the open transitions obtained at this
-intermediate step, constructed in a structural manner from all
-possible combinations of possible logical predicates, may
+The formal definitions and properties of the open pNets model were
+published in \cite{henrio:Forte2016}. In this new work we describe an implementation of
+the model and its semantics construction, including its interaction
+with the Z3 SMT engine.
+The implementation has two parts: the first is a finitary algorithm
+that builds all possible combinations of synchronisations through the
+pNet hierarchical structure. The result is a so-called
+\emph{open-automaton}, which transitions contains predicates relating
+the actions of the pNet holes and controllers. Some of the open
+transitions obtained at this step,  may
 contain predicates which do not represent any possible concrete
 instantiations. 
-Secondly, to get rid of these useless transitions, we use the SMT solver Z3 for checking the
+In the second part of the tool we use the SMT solver Z3 for checking the
 satisfiability of the predicate in each open transition. 
@@
 slighly bigger example, assembling 2 Failure controlers. We give some
-figures from this try in appendix~ref{}, showing that Z3 can check the
+figures from this try in appendix~\ref{appendix:scalingup}, showing that Z3 can check the
 satisfiablility of a 90K open transitions in a metter of minutes.
@@
 \subsection{Scaling up: several subsystems on the same bus}
+\label{appendix:scalingup}
 

### 2018-01-23 2017-Xudong-SMT/FM-2018-extended.tex
final...

@@
 
-Then we found some extra states that never found when running only the subnets.
-We figured out that is caused by a input mistake easily comparing it with the results on subnets.
+Analysing this result, we found some extra states that did not exist
+when running only the subnets.
+Comparing this with the previous result on on a single subnets, we
+found that this was caused by a input mistake in a synchronisation vector.
+
+After correction the algorithm produced 233280 OTs of which 281 are
+satisfiable. The resulting automaton has 17 reachable states. Of
+course we cannot display them here, and a model-checking tool would be
+required for their formal analysis.
+
 \end{document}

### 2018-01-23 2017-Xudong-SMT/FM-2018-extended.tex
Minor editing

--- 2018-01-23 2017-Xudong-SMT/FM-2018-extended.tex
@@
 \and INRIA Lille -- Nord Europe, 40 avenue Halley,
-59650 Villeneuve d'Ascq
+59650 Villeneuve d'Ascq,
 France}
@@
 function of the whole system.  
-No matter which module emits an "ask" to call for reset, the
-controller take the request. Then all of the modules are synchronised
-on the "reset". 
-So two more new transitions are added to the Timer to ensure the
+No matter which module emits an ``ask'' to call for a reset, the
+controller takes the request. Then all of the modules are synchronised
+on the ``reset''. 
+So two new transitions are added to the Timer to ensure the
 module can reset at any state.
 
-There are 327 satisfiable results, out of totally 97920 results, of
-the example computed in 105384 milliseconds (~1.45 minutes).
+In this example, there are 327 satisfiable predicates for the total of 97920 candidate open transitions, computed in 105384 milliseconds (~1.45 minutes). 
+The computation was carried out on an Intel Core i7 at 2.5GHz with 16GB of RAM.
+
+Analysing this result, we found some extra states that did not exist
+when running only the subnets.
+Comparing this with the previous result on on a single subnet, we
+found that this was caused by a input mistake in a synchronisation vector.
+
+After correction the algorithm produced 233280 OTs, whereof 281 are
+satisfiable. The resulting automaton has 17 reachable states. Of
+course we cannot display them here, and a model-checking tool would be
+required for their formal analysis.
 

### 2018-01-26 2016-Weak-FH-Bisim/WeakBisim.tex
correction + ajout comments

@@
 the mapping with a single entry $a$ at index $3$; exceptionally, such mappings with
-only a few entries will also be denoted $(3\mapsto a)$.
+only a few entries will also be denoted $(3\mapsto a)$. \TODO{We need to define update as $A \uplus \{j \mapsto a\}$ or $A[j \mapsto a]$}
 When this is not ambiguous, we shall use abusive vocabulary and
@@
 	\includegraphics[width=\linewidth]{XFIG/Bisim}
-	\TODO{change fig: s1,s2 $\to$ s,t}
+	\TODO{change fig: s1,s2 $\to$ s,t. DONE we will check if it is OK. Why did we use tilde notation for R}
 \end{minipage}
@@
 \end{definition}
+\TODO{$\uplus\{j_0\mapsto \pNet'\}$ non defini}
 
@@
        	\land v\!=\!v_{px} \land
-       	\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)$
-
-       	for any open transition $OT_{px}$, since
+       	\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)$\\
+
+For any open transition $OT_{px}$, since
        	$(t_p,u|\Pred_{p,u})\in\mathcal{R}'$ there exist open transitions
@@
        	(t_{px},u_{pxy}|\Pred_{{pxy}})\in \mathcal{R}'$; and  \\
-       	$\Pred_{p,u} \land \Pred_{OT_{p x}}\\
+       	$\Pred\,'_{p,u} \land \Pred_{OT_{p x}}\\
        	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
@@
        	\land v_{px}\!=\!v_{pxy} \land
-       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.
+       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$\\.
 
@@
        	More precisely, $t_{px} \in ({t'_p})^{p\in P'}$ where $({t'_p})^{p\in 
-       		P'}$ \TODO{Pas sure prime utile t, or p, or P ; SI:  $P\neq P'$ et 
-       		les $t_p'$ sont pas les $t_p$}
-       	is 
+       		P'}$ is 
        	the set of states relating ${s}'$ and $u_{pxy}$.
@@
        	\end{small}
-
+\TODO{From we will add notation (1) and (2)}        	
        	We have, for all $p$
@@
 
-By construction, the Post substitutions only have an effect on the  
+By construction, four substitutions $\subst{~}$ only have an effect on the  
 variables of the open automaton they belong to, they also produce terms containing only 
@@
        	\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
-       	= 
+       	\Leftrightarrow % we changed =
        	\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land
@@
        	\implies\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
-       	= \Pred\!'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}} $
+       	\Leftrightarrow % we changed = 
+       	 \Pred\!'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}} $\\
 
@@
 			{\ostate{s_i^{i\in L}} \OTarrow {v}
-				\ostate{s_i^{\prime i\in L}}}
+				\ostate{s_i'^{\, i\in L}}}
 		}
 	\]
-		with $Q$ ``moving'' (i.e. $J\cap\Holes(Q)\neq\emptyset$ or $I\cap L_Q\neq 
-		\emptyset$).
+		with $Q$ ``moving'' \TODO{or is reduced?}, i.e. $J\cap\Holes(Q)\neq\emptyset$ or $I\cap L_Q\neq 
+		\emptyset$.
 		 Then there exist $v_Q$, $\Pred\,'$, $\Pred\,''$, 
@@
 			{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I\setminus L_Q},
-				\{\xrightarrow{b_j}_j\}^{j\in J\setminus \Holes(Q) \cup \{j_0\}}, 
+				\{\xrightarrow{b_j}_j\}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
 				\Pred\,',  
@@
 			{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {v}
-				\ostate{s_i'^{\, i\in L\setminus L_Q}}}
+				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
 		}%\]
@@
 		Q\models{\inferrule*[myfraction=\reddottedrule]
-			{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I\cap L_Q},
+			{\{s_i\xrightarrow{a_i}_i s_i'\}^{\,i\in I\cap L_Q},
 				\{\xrightarrow{b_j}_j\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
@@
 			{\ostate{s_i^{i\in L_Q}} \OTarrow {v_Q}
-				\ostate{s_i'^{\, i\in L_Q}}}
+				\ostate{s_i'^{\,i\in L_Q}}}
 		}%\]
@@
 		and  $\Pred\subst{v_Q\leftarrow b_{j_0}} =(\Pred\,'
-		\land \Pred\,'')$, $\Post=\Post'\uplus 
+		\land \Pred\,'')$, $\Post=\Post\,'\uplus 
 		\Post\,''$ where $\Post\,''$ is the restriction of $\Post$ over variables of 
@@
 J_k})$. $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$. 
+\TODO{Revoir la def des leaves set ou multisets}
+
 Now focus on OTs of the subnets\footnotemark[\thefootnote]:\\[-2ex]
@@
 {\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
-	\ostate{s_{i}^{\prime\ i \in L_m}}}\]
+	\ostate{s_{i}'^{\, i \in L_m}}}\]
 Only elements of $I_k$ are useful to assert the premise for reduction of $P$; the last 
@@
 	}\]
+\TODO{We need to add: Note that $J_{j_0}=	J\cap\Holes(Q)$ this is a direct consequence of Tr2??}
+
 This already ensures the second part of the conclusion if we 
@@
 		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I \uplus I_Q},
-			\{\xrightarrow{b_j}_j\}^{j\in J\setminus\{j_0\} \uplus J_Q}, 
+			\{\xrightarrow{b_j}_j\}^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
 			\Pred\subst{b_{j_0}\leftarrow v_Q}\land\Pred\,',  
@@
 		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {v}
-			\ostate{s_i^{\prime i\in L\uplus L_Q}}}
+			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
 	}
@@
 $SV=clone(\alpha_j^{j\in I_k\uplus\{j_0\}\uplus 
-	J_k})$. $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$. All subpNets can be 
+	J_k})$. $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$. All sub-pNets can be 
 reduced:\\[-2ex]%\footnote{again we skip arguments related to renaming of fresh 
@@
 {\ostate{s_{i}^{i \in L_k}} \OTarrow {v_m}
-	\ostate{s_{i}^{\prime\ i \in L_k}}}\]
+	\ostate{s_{i}'^{\, i \in L_k}}}\]
 the last sub-pNet is the one filled by $Q$ which offers an open transition by hypothesis.
@@
  We will consider the relation $\mathcal{R}'=\{(s,t|\Pred_{s,t})|s=s'\uplus s'' \land 
- t=t'\uplus s'' \land s''\in \mathcal{S}_P \land (s',t'|\Pred_{s,t})\in\mathcal{R}\}$ 
+ t=t'\uplus s'' \land s''\in \mathcal{S}_P \land (s',t'|\Pred_{s,t})\in\mathcal{R}\}$ \TODO{$\uplus$ entre states?} 
  where $\mathcal{S}_S$ is the set of states of the open automaton of $P$.	We will prove 
@@
  		\Pred\,',  
- 		\Post'}
+ 		\Post\,'}
  	{\ostate{s_{i}^{i\in L_P}} \OTarrow {v}
- 		\ostate{s_{i}'^{~ i\in L_P}}}
+ 		\ostate{s_{i}'^{\,i\in L_P}}}
  }\\
@@
  		\{\xrightarrow{b_j}_j\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
- 		\Post''}
+ 		\Post\,''}
  	{\ostate{s_{i}^{i\in L}} \OTarrow {v_Q}
- 		\ostate{s_{i}'^{~ i\in L}}}
+ 		\ostate{s_{i}'^{\,i\in L}}}
  }\end{mathpar}
@@
  \land v_Q\!=\!v_x \land  
- \Pred_{s x}\subst{\Post''}\subst{\Post_{OT_x}}\right)$
+ \Pred_{s x}\subst{\Post\,''}\subst{\Post_{OT_x}}\right)$
 
@@
 					\Pred\,',  
-					\Post'}
+					\Post\,'}
 				{\ostate{s_{1}^{i\in L}} \OTarrow {v}
@@
 					\{\xrightarrow{b_j}_j\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
-					\Post''}
+					\Post\,''}
 				{\ostate{s_{i}^{i\in L_Q}} \OTarrow {v_Q}
@@
 			and  $\Pred_{OT}\subst{v_Q\leftarrow b_{j_0}} =({\Pred\,}'
-			\land {\Pred\,}'')$, $\Post_{OT}=\Post'\uplus 
-			\Post''$ ($\Post''$ is the restriction of $\Post$ over variables of 
+			\land {\Pred\,}'')$, $\Post_{OT}=\Post\,'\uplus 
+			\Post\,''$ ($\Post\,''$ is the restriction of $\Post$ over variables of 
 			$\Leaves(Q)$). As $P$ is FH-bisimilar to $P'$ and $(\ostate{s_{i}^{i \in 
@@
 			\land v\!=\!v_x \land  
-			\Pred_{s x}\subst{\Post'}\subst{\Post_{OT_x}}\right)$
+			\Pred_{s x}\subst{\Post\,'}\subst{\Post_{OT_x}}\right)$
 			%     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x}) \right)$.
@@
 						\Pred_{OT_x}\subst{b_{j_0 x}\leftarrow v_Q}\land\Pred\,'',  
-						\Post_{OT_x}\uplus \Post''}
+						\Post_{OT_x}\uplus \Post\,''}
 					{\ostate{t_{ i }^{i\in L'\uplus L_Q}} \OTarrow {v_x}
@@
 \land v\!=\!v_x}} %\\ \hspace*{40mm} %
-\land \Pred_{s x}\subst{\Post'}\subst{\Post_{OT_x}}) \land
+\land \Pred_{s x}\subst{\Post\,'}\subst{\Post_{OT_x}}) \land
 \Pred\,''\\ % 
@@
 \!\land\! v\!=\!v_x \!\land\!  
-\Pred_{s x}\subst{\Post'}\subst{\Post_{OT_x}})}} 			
+\Pred_{s x}\subst{\Post\,'}\subst{\Post_{OT_x}})}} 			
 $\end{small}
@@
 	change the validity of the formula (those variables are not used).
-	\item We need $\Pred_{s x}\subst{\Post_{OT}}\subst{\Post_{OT_x}\uplus \Post''}$ 
-	, i.e.:
-	$\Pred_{s x}\subst{\Post'\uplus \Post''}\subst{\Post_{OT_x}\uplus \Post''}$. We 
+	\item We need $\Pred_{s x}\subst{\Post_{OT}}\subst{\Post_{OT_x}\uplus \Post\,''}$, i.e.:
+	$\Pred_{s x}\subst{\Post\,'\uplus \Post\,''}\subst{\Post_{OT_x}\uplus \Post\,''}$. We 
 	can conclude by observing that	$\Pred_{s x}$ does not use any variable of $Q$ 
-	and thus $\subst{\Post''}$ has no effect.
+	and thus $\subst{\Post\,''}$ has no effect.
 \end{itemize}	

### 2018-02-02 2017-Xudong-SMT/FM-2018-extended-RR.tex
First elements for elimination

--- 2018-01-23 2017-Xudong-SMT/FM-2018-extended.tex
@@
 
-\title{Using SMT engine to generate Symbolic Automata\thanks{This work was partially 
+\title{Using SMT engine to generate Symbolic Automata - Extended version\thanks{This work was partially 
 funded by the Associated Team FM4CPS
@@
 For example, in the running example, in the raw output listing in
-Appendix~ref{}, in the first OT, you find variables: 
+Appendix~\ref{appendix:fullOutput}, in the first OT, you find variables: 
 \begin{itemize}
@@
 
-In this example, there are 327 satisfiable predicates for the total of 97920 candidate open transitions, computed in 105384 milliseconds (~1.45 minutes). 
+In this example, there are 327 satisfiable predicates for the total of 97920 candidate open transitions, computed in 105384 milliseconds (\textasciitilde{}1.45 minutes). 
 The computation was carried out on an Intel Core i7 at 2.5GHz with 16GB of RAM.
@@
 
-\end{document}
+%\end{document}
 
 \subsection{Simplification of Predicates}
-\TODO{I keep it here for now, but I think we shall not include it in
-  the FM submission, this section is not mature enough}
 
@@
 Before:
+\ERIC{Also this OT is not the real original one (as in RoughResult.log), pieces have already been simplied...}
+
       \begin{mathpar}
@@
 
-\QIN{
-We want to reason about the equations to eliminate the redundancy. 
-Considering pNet has a special tree-structure, the replacement between equations should be one-way, the direction is from leaves to the top level, until the root pNet node. 
+\TODO{
+
+% We want to reason about the equations to eliminate the redundancy. 
+% Considering pNet has a special tree-structure, the replacement between equations should be one-way, the direction is from leaves to the top level, until the root pNet node. 
 And it is easy to figure out the intermediate variables by the constraint rules.
-While it is not needed figure out if an equation is "true" , it can be left to Z3.
-}
+% While it is not needed figure out if an equation is "true" , it can be left to Z3.
 
@@
 
-\paragraph{Term Rewriting Rules}
-Predicates already have a format declaring what it verifies. According to that previous work, we define the predicates.
-Let $\mylangle\overline{\pNet},\overline{S},\symb{SV}_k^{k\in K} \myrangle$
-be a pNet. Choose a synchronisation vector $SV=clone(SV_k) ={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v' \, ,G_k $, for $k\in K$. The
-predicate $\Pred$ relating
-the actions of the involved sub-pNets and the resulting actions.
-\begin{definition}[Predicate]
-\[\Pred(SV, \overline{\pNet},\overline{S}, v) = 
-\begin{array}{l}
-\forall {(a'_i)}^{i\in I},
-{(b'_j)}^{j\in J},v'.
-\\
-v_m=a'_i\land \, b_j=b'_j \land v=v' \land G_k
-\end{array}\]
-\end{definition}
-\QIN{
-The new predicates introduce more hypotheses for term rewriting. However, not every variable can be substituted. 
-Here we introduce several rewriting rules.
-}
-
-\begin{align*}
-   &v_m=a'_i \land v_m=v'_m \rightarrow a'_i = v'_m &[RL-1]\\\\
-   &v_m=a'_i \land v=v' \rightarrow v_m=v ~~ \texttt{if} ~~ a'_i = v', ~~ a'_i,v' \in InterVar &[RL-2]\\\\
-   &v_m=foo'_i(a_1,...,a_p,...,a_n) \land v=v' \rightarrow v_m=foo'_i(a_1,...,v,...,a_n) \\ 
-   &\hspace{15em}\texttt{if} ~~ a_p = v', ~~ a_p,v \in InterVar &[RL-3]\\\\
-   &b_j=b'_j \land v=v' \rightarrow b_j=v ~~ \texttt{if} ~~ b'_j = v', ~~ b'_j,v' \in InterVar &[RL-4]\\\\
-   &b_j=foo'_i(a_1,...,a_p,...,a_n) \land v=v' \rightarrow b_j=foo'_i(a_1,...,v,...,a_n) \\ 
-   &\hspace{15em}\texttt{if} ~~ a_p = v', ~~ a_p,v \in InterVar &[RL-5]\\\\
-\end{align*}
-
-\QIN{
-Rule RL-1 applies on when the result action of subnets matching other arguments of the chosen SV. It merges the predicates from the subnets with the new generated predicates.
-Rule RL-2 shows that if the result of the SV is also in its arguments, we can straightly get an equation between the subnet action and  the result action.
+%% \paragraph{Term Rewriting Rules}
+%% Predicates already have a format declaring what it verifies. According to that previous work, we define the predicates.
+%% Let $\mylangle\overline{\pNet},\overline{S},\symb{SV}_k^{k\in K} \myrangle$
+%% be a pNet. Choose a synchronisation vector $SV=clone(SV_k) ={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v' \, ,G_k $, for $k\in K$. The
+%% predicate $\Pred$ relating
+%% the actions of the involved sub-pNets and the resulting actions.
+%% \begin{definition}[Predicate]
+%% \[\Pred(SV, \overline{\pNet},\overline{S}, v) = 
+%% \begin{array}{l}
+%% \forall {(a'_i)}^{i\in I},
+%% {(b'_j)}^{j\in J},v'.
+%% \\
+%% v_m=a'_i\land \, b_j=b'_j \land v=v' \land G_k
+%% \end{array}\]
+%% \end{definition}
+%% \QIN{
+%% The new predicates introduce more hypotheses for term rewriting. However, not every variable can be substituted. 
+%% Here we introduce several rewriting rules.
+%% }
+
+%% \begin{align*}
+%%    &v_m=a'_i \land v_m=v'_m \rightarrow a'_i = v'_m &[RL-1]\\\\
+%%    &v_m=a'_i \land v=v' \rightarrow v_m=v ~~ \texttt{if} ~~ a'_i = v', ~~ a'_i,v' \in InterVar &[RL-2]\\\\
+%%    &v_m=foo'_i(a_1,...,a_p,...,a_n) \land v=v' \rightarrow v_m=foo'_i(a_1,...,v,...,a_n) \\ 
+%%    &\hspace{15em}\texttt{if} ~~ a_p = v', ~~ a_p,v \in InterVar &[RL-3]\\\\
+%%    &b_j=b'_j \land v=v' \rightarrow b_j=v ~~ \texttt{if} ~~ b'_j = v', ~~ b'_j,v' \in InterVar &[RL-4]\\\\
+%%    &b_j=foo'_i(a_1,...,a_p,...,a_n) \land v=v' \rightarrow b_j=foo'_i(a_1,...,v,...,a_n) \\ 
+%%    &\hspace{15em}\texttt{if} ~~ a_p = v', ~~ a_p,v \in InterVar &[RL-5]\\\\
+%% \end{align*}
+
+%% \QIN{
+%% Rule RL-1 applies on when the result action of subnets matching other arguments of the chosen SV. It merges the predicates from the subnets with the new generated predicates.
+%% Rule RL-2 shows that if the result of the SV is also in its arguments, we can straightly get an equation between the subnet action and  the result action.
 RL-3 is the situation that there is an expression instead of a variable contains an intermediate argument.
 The substitution will only occur on the argument.
-Actually, what happened is similar if there is a hole behaviour instead of a subnet result action attending in the equation.
+%% Actually, what happened is similar if there is a hole behaviour instead of a subnet result action attending in the equation.
 So we get RL-4 and RL-5.
@@
 That's why there no rule similar to the RL-1 for hole behaviours.
-}
+%% }
+
+\end{document}

### 2018-02-05 2018-Arch-pNets/arch-pNets.tex
Added the paper extending architectures with data (2018-Arch-pNets) to the repo

% This is LLNCS.DOC the documentation file of
% the LaTeX2e class from Springer-Verlag
% for Lecture Notes in Computer Science, version 2.4
\documentclass{llncs}
\usepackage{llncsdoc}

%\usepackage{a4wide}

\usepackage{graphicx}
\usepackage{verbatim}

\let\proof\relax   
\let\endproof\relax

\usepackage{amsmath,amsthm,amscd}
\usepackage{amssymb}  %for blackboard B
\usepackage{rotating} %to rotate the figures
\usepackage{mathpartir} % math paragraph + inference rules
\usepackage{caption}
\usepackage{xifthen}
\usepackage{stmaryrd} % double brackets (\llbracket, \rrbracket)

%% \usepackage[justification=centering,belowskip=-10pt,aboveskip=0pt]{caption}
%% \setlength{\intextsep}{10pt plus 2pt minus 2pt}
%% \setlength\abovedisplayskip{0pt}

\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{hyperref}

\usepackage{soul}
\usepackage[colorinlistoftodos,bordercolor=white]{todonotes}
%% \usepackage[disable,colorinlistoftodos,bordercolor=white]{todonotes}

\newcommand{\Simon}{\\\hfill\mdash Simon}

\newcommand{\noteSB}[2][color=green!40, size=\tiny]{\todo[#1]{{#2}\Simon}}
\newcommand{\noteSBin}[2][inline,color=green!40]{\todo[#1]{{#2}\Simon}}
\newcommand{\todoSB}[2][color=green!40, size=\tiny]{\todo[#1]{\textbf{To-do Simon:} {#2}}}
\newcommand{\todoSBin}[2][inline,color=green!40]{\todo[#1]{\textbf{To-do Simon: } {#2}}}

\newcommand{\defn}[1]{Def.~\ref{defn:#1}}
\newcommand{\defntwo}[2]{Defs~\ref{defn:#1} and \ref{defn:#2}}
\newcommand{\fig}[1]{Fig.~\ref{fig:#1}}
\newcommand{\figs}[2]{Fig.~\ref{fig:#1} and~\ref{fig:#2}}
\newcommand{\tab}[1]{Tab.~\ref{tab:#1}}
\newcommand{\eq}[1]{(\ref{eq:#1})}
\newcommand{\res}[1]{(\ref{res:#1})}
\newcommand{\ex}[1]{Ex.~\ref{ex:#1}}
\newcommand{\exs}[2]{Ex.~\ref{ex:#1} and~\ref{ex:#2}}
\newcommand{\secn}[1]{Sect.~\ref{secn:#1}}
\newcommand{\rem}[1]{Rem.~\ref{rem:#1}}
\newcommand{\lem}[1]{Lem.~\ref{lem:#1}}
\newcommand{\cor}[1]{Cor.~\ref{cor:#1}}
\newcommand{\thm}[1]{Th.~\ref{thm:#1}}
\newcommand{\axs}[1]{Ax.~\ref{ax:#1}}
% \newcommand{\ax}[2]{\ref{ax:#1}.\ref{ax:#1:#2}}
\newcommand{\ax}[1]{Ax.~\ref{ax:#1}}
\newcommand{\prop}[1]{Prop.~\ref{prop:#1}}
\newcommand{\alg}[1]{Alg.~\ref{alg:#1}}
\newcommand{\asmp}[1]{Ass.~\ref{asmp:#1}}

% %%%%%%%%%%%%%%%%%%%%%

\newcommand{\cA}{\ensuremath{\mathcal{A}}}
\newcommand{\bB}{\ensuremath{\mathbf{B}}}
\newcommand{\cB}{\ensuremath{\mathcal{B}}}
\newcommand{\sB}{\ensuremath{\mathbb{B}}}
\newcommand{\cC}{\ensuremath{\mathcal{C}}}
\newcommand{\sC}{\ensuremath{\mathbb{C}}}
\newcommand{\cD}{\ensuremath{\mathcal{D}}}
\newcommand{\fD}{\ensuremath{\mathsf{D}}}
\newcommand{\sD}{\ensuremath{\mathbb{D}}}
\newcommand{\cE}{\ensuremath{\mathcal{E}}}
\newcommand{\sE}{\ensuremath{\mathbb{E}}}
\newcommand{\cF}{\ensuremath{\mathcal{F}}}
\newcommand{\cG}{\ensuremath{\mathcal{G}}}
\newcommand{\cH}{\ensuremath{\mathcal{H}}}
\newcommand{\cI}{\ensuremath{\mathcal{I}}}
\newcommand{\sI}{\ensuremath{\mathbb{I}}}
\newcommand{\cM}{\ensuremath{\mathcal{M}}}
\newcommand{\cN}{\ensuremath{\mathcal{N}}}
\newcommand{\sN}{\ensuremath{\mathbb{N}}}
\newcommand{\cP}{\ensuremath{\mathcal{P}}}
\newcommand{\sP}{\ensuremath{\mathbb{P}}}
\newcommand{\cQ}{\ensuremath{\mathcal{Q}}}
\newcommand{\sQ}{\ensuremath{\mathbb{Q}}}
\newcommand{\cR}{\ensuremath{\mathcal{R}}}
\newcommand{\sR}{\ensuremath{\mathbb{R}}}
\newcommand{\cS}{\ensuremath{\mathcal{S}}}
\newcommand{\sS}{\ensuremath{\mathfrak{S}}}
\newcommand{\cT}{\ensuremath{\mathcal{T}}}
\newcommand{\fT}{\ensuremath{\mathsf{T}}}
\newcommand{\sT}{\ensuremath{\mathbb{T}}}
\newcommand{\cV}{\ensuremath{\mathcal{V}}}
\newcommand{\fV}{\ensuremath{\mathsf{V}}}
\newcommand{\sV}{\ensuremath{\mathbb{V}}}
\newcommand{\sZ}{\ensuremath{\mathbb{Z}}}

\newcommand{\mdash}[1][]{---#1}
\newcommand{\ndash}{--}
\newcommand{\ie}[1][\ ]{i.e.#1}
\newcommand{\etc}[1][\ ]{etc.#1}
\newcommand{\eg}[1][\ ]{e.g.#1}
\newcommand{\cf}[1][\ ]{cf.#1}
\newcommand{\wrt}[1][\ ]{w.r.t.#1}

\newcommand{\bydef}[1]{\ensuremath{\stackrel{\mathit{\scriptscriptstyle def}}{#1}}}
\newcommand{\suchthat}{\ensuremath{\,|\,}}
\newcommand{\rightsuchthat}{\ensuremath{\,\right|\,}}
\newcommand{\leftsuchthat}{\ensuremath{\,\left|\,}}
\newcommand{\setdef}[2]{\ensuremath{\{{#1}\,|\,{#2}\}}}
\newcommand{\setdefb}[2]{\ensuremath{\bigl\{{#1}\,\bigl|\,{#2}\bigr.\bigr\}}}
\newcommand{\Setdef}[2]{\ensuremath{\Big\{{#1}\,\Big|\,{#2}\Big\}}}
\newcommand{\goesto}[2][]{\ensuremath{\xrightarrow[#1]{#2}}}
\newcommand{\notgoesto}[2][]{\ensuremath{\not\xrightarrow[#1]{\ \,#2}}}
\newcommand{\non}[1]{\ensuremath{\overline{#1}}}

\newcommand{\true} {\ensuremath{\mathtt{t\!t}}}
\newcommand{\false}{\ensuremath{\mathtt{f\!f}}}
\newcommand{\noop} {\ensuremath{\mathsf{skip}}}

\newcommand{\data}{\ensuremath{\sD}}
\newcommand{\guards}[1]{\ensuremath{\sB_{#1}}}
\newcommand{\exprs}[1]{\ensuremath{\sE_{#1}}}
\newcommand{\valuations}[1]{\ensuremath{\sV_{#1}}}
\newcommand{\val}[3][]{%
  \ensuremath{\sigma^{#2}_{#3}%
    \ifthenelse{\isempty{#1}}{}{(#1)}%
  }%
}
%% \DeclareMathOperator{\supp}{supp}
\newcommand{\supp}[1]{\ensuremath{\mathrm{supp}(#1)}}
\newcommand{\semopen}[1]{\ensuremath{[{#1}]}}
\newcommand{\semclosed}[1]{\ensuremath{\llbracket{#1}\rrbracket}}
\newcommand{\reachable}[1]{\ensuremath{\mathit{reachable}({#1})}}
\newcommand{\IMextend}[2]{\ensuremath{#1 \ltimes #2}}

% %%%%%%%%%%%%%%%%%%%%%

\usepackage{tikz}
\usetikzlibrary{calc}
\usetikzlibrary{arrows,shapes,automata,petri}
  \tikzset{
  place/.style={
    circle,
    thick,
    draw=blue!75,
    fill=blue!20,
    minimum size=6mm
  },
  transition/.style={
    rectangle,
    thick,
    fill=black,
    minimum width=8mm,
    inner ysep=2pt
    },
    arc/.style = {
      decoration=
      {markings,mark=at position #1 with {circle;}
      },
      postaction={decorate,draw}},
  }

\let\llncssubparagraph\subparagraph
\let\subparagraph\llncssubparagraph

\begin{document}
\graphicspath{{figures/}}

\title{Architectures and Open pNets}

\author{%
Simon~Bliudze\inst{1}
\and
Ludovic~Henrio\inst{2}
\and
Eric~Madelaine\inst{3}
\and
...
}

\institute{%
  INRIA Lille -- Nord Europe, Villeneuve d'Ascq, France\\
  \email{simon.bliudze@inria.fr}
\and
\and
}

\maketitle

\begin{abstract}
  We extend the theory of architectures with a general
  mechanism for handling various types of data transfer.  We
  encode this extended model into the open pNet semantic
  model and show how this encoding can be used to verify
  that an architecture does, indeed, enforce its
  characteristic property.

\keywords{}
\end{abstract}

%***********************************************************
%***********************************************************

\section{Introduction}
\label{secn:introduction}

%***********************************************************
%***********************************************************

\section{The theory of architectures with data}
\label{secn:archs}

%***********************************************************

\subsection{Components and composition}
\label{sec:components}

\todoSBin{Preliminaries on the universal(?) data domain $\data$
  and valuations.}

\begin{definition}[Components]
  \label{defn:component}
  A \emph{component} is a tuple $(Q, q^0, P, V, \val{0}{},
  \goesto{})$, where
  \begin{itemize}
  \item $Q$ is a set of \emph{states}, with $q^0 \in Q$ the
    \emph{initial state}, 
  \item $P$ is a set of \emph{ports},
  \item $V$ is a set of \emph{component variables},
  \item $\val{0}{} : V \rightarrow \data$ is an \emph{initial
    valuation} of the component variables, 
  \item $\goesto{}\, \subseteq
    Q \times 2^P \times \guards{V} \times \exprs{V} \times Q$
%
    is a \emph{transition relation}, with transitions
    labelled by triples consisting of an \emph{interaction}
    $a \subseteq P$, a Boolean \emph{guard} $g \in
    \guards{V}$ and an \emph{update expression} $e \in
    \exprs{V}$.
  \end{itemize}
%
  We call the pair of sets $(P,V)$ the \emph{interface} of the
  component.\,\footnote{%
%
  In practice, component variables are split in two sub-sets:
  local and exported variables.  Only exported variables belong
  to the component interface and can be used for the interactions
  with other components (see \defn{im}).  However, in the context
  of this paper we can simplify by omitting this separation.
%
  }
%
  Notations $q \goesto{a} q'$, $q \goesto{a}$ and $q
  \notgoesto{a}$ are as usual; for a component $B$, we denote
  $Q_B$, $q^0_B$, $P_B$, $V_B$, $\val{0}{B}$ and $\goesto[B]{}$
  the constituents of $B$.
\end{definition}

\begin{definition}[Component semantics]
  \label{defn:comp:semantics}
  The \emph{open semantics} of a component $B = (Q, q^0, P, V,
  \val{0}{}, \goesto{})$ is given by the LTS $\semopen{B} = (S,
  s^0, \goesto{})$, where $S = Q \times \valuations{V}$, $s^0 =
  (q^0, \val{0}{})$ and $\goesto{}$ is the minimal transition
  relation satisfying the following rule:
  %
  \begin{equation}
    \label{eq:comp:semantics}
    \infer{
      q \goesto{a, g, e} q'
      \and
      v \models g
      \and
      v' = v[e]
    }{
      (q, v) \goesto{a} (q', v')
    }
    \,.
  \end{equation}
  The \emph{closed semantics} of $B$ is given by the LTS
  $\semclosed{B} \bydef{=}\reachable{\semopen{B}}$, comprising
  only the reachable states of $\semopen{B}$.
\end{definition}

\begin{definition}[Interaction model \& composition]
  \label{defn:im}
  Let $\cB = \{B_1,\dots,B_n\}$ be a finite set of
  components with $B_i = (Q_i, q^0_i, P_i, V_i, \val{0}{i},
  \goesto{})$,\footnote{%
%
    Here and below, we skip the index on the transition
    relation $\goesto{}$, since it is always clear from the
    context.
%
} such that all their respective components (\ie $Q_i$, $P_i$,
  and $V_i$) are pairwise disjoint, \ie $\forall i \neq j,\ Q_i
  \cap Q_j = P_i \cap P_j = V_i \cap V_j = \emptyset$.  Let $P =
  \bigcup_{i = 1}^n P_i$ and $V = \bigcup_{i = 1}^n V_i$.

  An \emph{interaction model over $(P,V)$} is a set $\Gamma
  \subseteq 2^P \times \guards{V} \times \exprs{V}$, such that,
  for any $(a, g, e) \in \Gamma$, the guard and update expression
  associated to the \emph{interaction} $a$ satisfy, respectively,
  $g \in \guards{V_a}$ and $e \in \exprs{V_a}$, with $V_a
  \bydef{=} \bigcup_{i:\, a \cap P_i \neq \emptyset} V_i$.  We
  denote $\supp{a} \bydef{=} \setdef{i \in [1,n]}{a \cap P_i \neq
    \emptyset}$ the \emph{support} of the interaction $a$.
  %% We call the set of ports $P$ the \emph{domain} of the
  %% interaction model.

  The \emph{composition of $\cB$ with the interaction model
    $\Gamma$} is the component $\Gamma(\cB) = (Q, q^0, P, V,
  \val{0}, \goesto{})$, where $Q = \prod_{i=1}^n Q_i$, $q^0 =
  q_1^0\dots q_n^0$, $\val{0}{}: V \rightarrow \data$ is such
  that, for any $v \in V_i$, $\val[v]{0}{} = \val[v]{0}{i}$, and
  $\goesto{}$ is the minimal transition relation satisfying
  following rules:
%
  \begin{mathpar}
    \infer{
      q_i \goesto{\emptyset, \true, \noop} q_i'
    }{
      q_1 \dots q_i \dots q_n \goesto{\emptyset, \true, \noop} q_1 \dots q_i' \dots q_n
    }\,,

    \infer{    
      (a, g, e) \in \Gamma
      \and
      \forall i \in \supp{a}, q_i \goesto{a \cap P_i, g_i, e_i} q_i'
      \and
      \forall i \not\in \supp{a}, q_i = q_i'
      \\\\
      G = g \land \bigwedge_{i \in \supp{a}} g_i
      \and
      E = e; (e_i)_{i \in \supp{a}}
    }{
      q_1\dots q_n \goesto{a, G, E} q_1'\dots q_n'
    }\,.
  \end{mathpar}
\end{definition}

Below, when speaking of a set of components $\cB$, we will always
assume that it satisfies all the assumptions of \defn{im}.
%
For an interaction $a$, we will abuse the notation by writing
$\supp{a}$ to also denote the set $\setdef{B \in \cB}{a \cap P_B
  \neq \emptyset}$.  The precise meaning of this notation will
always be clear from the context.

%***********************************************************
\subsection{Architectures}
\label{secn:archi}

\begin{definition}[Architecture]
  \label{defn:arch}
  An \emph{architecture} is a tuple $A = (\cC, P_A, V_A, \Gamma)$,
  where $\cC$ is a finite set of \emph{coordinating components}
  with pairwise disjoint sets of ports and variables, such that
  $\bigcup_{C \in \cC} P_C \subseteq P_A$ and
  $\bigcup_{C \in \cC} V_C \subseteq V_A$, and
  $\Gamma \subseteq 2^{P_A} \times \guards{V_A} \times \exprs{V_A}$
  is an interaction model over $(P_A, V_A)$.
\end{definition}

\begin{definition}[Application of an architecture]
  \label{defn:arch:application}
  Let $A = (\cC, P_A, V_A, \Gamma)$ be an architecture and let $\cB$
  be a set of components, such that
%
  \begin{align}
    \bigcup_{B \in \cB} P_B \cap \bigcup_{C \in \cC} P_C = \emptyset\,,
    &&
    P_A \subseteq P \bydef{=} \bigcup_{B \in \cB \cup \cC} P_B\,,
    \\
    \bigcup_{B \in \cB} V_B \cap \bigcup_{C \in \cC} V_C = \emptyset\,,
    &&
    V_A \subseteq V \bydef{=} \bigcup_{B \in \cB \cup \cC} V_B\,,
  \end{align}
%
  and, denoting, for any $(a, g, e) \in \Gamma$, $V_a \bydef{=}
  \bigcup_{B \in \supp{a}} V_B$, we have $g \in \guards{V_a}$ and
  $e \in \exprs{V_a}$.
%
  The \emph{application of the architecture $A$ to the set of
  components $\cB$} is the component $ A(\cB) \bydef{=}
  (\IMextend{\Gamma}{P})(\cC \cup \cB)$, where
%
  \begin{equation}
    \label{eq:im:extension}
    \IMextend{\Gamma}{P} \bydef{=}
    \setdefb{
      (a \cup a', g, e)
    }{
      (a, g, e) \in \Gamma, a' \subseteq P \setminus P_A
    }
  \end{equation}
%
  denotes the \emph{extension} of the interaction model $\Gamma$
  to the set of ports $P$.
\end{definition}

An architecture $A$ enforces coordination constraints on the
components in $\cB$.  The interface $(P_A, V_A)$ of an
architecture $A$ contains all ports of the coordinating
components $\cC$ and some additional ports, which must belong to
the components in $\cB$.  In the application $A(\cB)$, the ports
belonging to $P_A$ can only participate in the interactions
defined by the interaction model $\Gamma$ of $A$.  Ports which do
not belong to $P_A$ are not restricted and can participate in any
interaction.  In particular, they can join the interactions in
$\Gamma$ (see \eq{im:extension}).  If the interface of the
architecture covers all ports of the system, \ie $P = P_A$, we
have $P\setminus P_A = \emptyset$ and the only interactions
allowed in $A(\cB)$ are those belonging to $\Gamma$.  Notice also
that the restrictions imposed by \defn{archi:application} on the
set of operand components $\cB$ ensure that an interaction in
$\IMextend{\Gamma}{P}$ can only refer to variables of the
participating components.
%
Finally, the definition of $\IMextend{\Gamma}{P}$ requires that
an interaction from $\Gamma$ be involved in every interaction
belonging to $\IMextend{\Gamma}{P}$.  To allow the ports from $P
\setminus P_A$ to be fired independently in $A(\cB)$, one must
have $(\emptyset, \true, \noop) \in \Gamma$.

\begin{definition}[Composition of architectures]
  \label{defn:arch:composition}

\end{definition}

%***********************************************************
%***********************************************************

\section{Open pNets}
\label{secn:pNets}

%***********************************************************
%***********************************************************

\section{Encoding of architectures into open pNets}
\label{secn:encoding}

%***********************************************************
%***********************************************************

\section{SMT encoding of open pNets}
\label{secn:smt}

%***********************************************************
%***********************************************************

\section{Case study}
\label{secn:case-study}

%***********************************************************
%***********************************************************

\section{Related work}
\label{secn:related}

%***********************************************************
%***********************************************************

\section{Conclusion}
\label{secn:conclusion}

%***********************************************************
%***********************************************************

\bibliographystyle{abbrv}
\bibliography{}

\end{document}

### 2018-02-05 2017-Xudong-SMT/bisimulation.tex

--- 2017-11-22 2017-Xudong-SMT/checker.tex
@@
 \usepackage{amsmath,amssymb,amscd,mathrsfs}
-\usepackage{array,booktabs,arydshln,xcolor}
 \DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
@@
 
-\usepackage{macrospNets}
+%\usepackage{macrospNets}
+
+\def\R{\mathcal{R}}
 
@@
 \pagestyle{plain}
+
 % addition to the mathpartir package for red dotted rules,
 % that we use for open-transitions
+
 \makeatletter
@@
 \newcommand{\sm}[1]{\mbox{\boldmath\small #1}}
+
 \DeclareMathOperator{\card}{card}
@@
 \begin{document}
-\section{Type system}
-The SMT solver Z3 already has conservative type rules and checks type safety in Horn logic. When translating the pNets into SMT-LIB language, pNets should also make sure that
-the term matching other term in SMT-LIB language will be correct in type checking. In next two section, we give out the presentation of the pNets and the type rules of them to ensure the type safety. 
-\subsection{Algebra Presentation}
-We have a set of basic algebra presentation for the pNet, including three basic sorts $Bool$, $Action$ and $Int$ and their own operators(constants as operators with no argument).
-\begin{table}\caption{\leftline{Algebra Presentation}}
-	\begin{tabular}{p{4cm}p{8cm}}
-		\hline\specialrule{0em}{1pt}{1pt}
-		Sort & Operator \\\specialrule{0em}{1pt}{1pt}
-		\hdashline\specialrule{0em}{3pt}{3pt}
-		Bool    			& $=,\ \ne,\ \land,\ \lor,\ \texttt{true},\ \texttt{false},\ \texttt{FUN}$ 								\\\specialrule{0em}{1pt}{1pt}
-		Action 			& $=,\ \ne,\ \texttt{FUN}$ 																	\\\specialrule{0em}{1pt}{1pt}
-		Int 				& $=,\ \ne,\ - \texttt{(unary)},\ +,\ - \texttt{(binary)},\ \times,\ \div,\ \texttt{Nat},\ \texttt{FUN}$ 			\\\specialrule{0em}{1pt}{1pt}
-		\hline
-	\end{tabular}
-\end{table}
 
-\subsection{Type Rule}
-The environment is a set of variables with their own types like $x_1 : A_1, ...
-, x_n : A_n$.
-And use dom$(\Gamma)$ dedicate the collection of $x_1, ...
-, x_n$.
-Let $\mathcal{P}$ to be the presentation of the pNet.
-\begin{table}\caption{\leftline{Judgments for Open pNets}}
-	\begin{tabular}{p{5cm}p{7cm}}
-		\hline\specialrule{0em}{3pt}{3pt}
-		$\Gamma \vdash \diamond$ 					& $\Gamma$ is a well-formed environment 					\\\specialrule{0em}{1pt}{1pt}
-		$\Gamma \vdash A$ 							& A is a well-formed type in $\Gamma$	 					\\\specialrule{0em}{1pt}{1pt}
-		$\Gamma \vdash M: A$ 						& M is a well-formed term of type A in $\Gamma$			\\\specialrule{0em}{1pt}{1pt}
-		\specialrule{0em}{3pt}{3pt}\hline
-	\end{tabular}
-\end{table}
+\section{Current State of Bisimulation}
+There are two new classes added in the $\texttt{fr.inria.oasis.vercors.vce.openpnets.prover}$.
+\begin{itemize}
+	\item $Relation$ is the input for bisimulation checking.
+	\item $BisimulationChecker$ generate the proof obligation and submit it to the Z3 solver to check.
+\end{itemize}
 
-\begin{table}\caption{\leftline{Type Rules for Open pNets}}
-	\begin{tabular}{p{5cm}p{5cm}p{2.5cm}}
-		\hline\specialrule{0em}{3pt}{3pt}
-		(Env $\varnothing$) 								
-		& 										
-		&					\\\specialrule{0em}{1pt}{1pt}
-            $\dfrac{ }{\varnothing \vdash \diamond}$			
-            & %$\dfrac{\Gamma \vdash A ~~ x\ }{\varnothing \vdash \diamond}$
-            &					\\\specialrule{0em}{3pt}{3pt}
-		(Type Bool) 										
-		&(Type Action) 						
-		&(Type Int)			\\\specialrule{0em}{1pt}{1pt}
-		$\dfrac{\mathcal{P} \vdash Bool~~\Gamma \vdash \diamond}{\mathcal{P},\Gamma \vdash Bool}$ 
-		& $\dfrac{\mathcal{P} \vdash Action~~\Gamma \vdash \diamond}{\mathcal{P},\Gamma \vdash Action}$ 
-		& $\dfrac{\mathcal{P} \vdash Int~~\Gamma \vdash \diamond}{\mathcal{P},\Gamma \vdash Int}$        \\\specialrule{0em}{3pt}{3pt}
-		(Var x) 										
-		& 						
-		&			\\\specialrule{0em}{1pt}{1pt}
-		$\dfrac{\mathcal{P} \vdash A~~\Gamma \vdash x:A}{\mathcal{P},\Gamma \vdash x:A}$ 
-		&  
-		&       		\\\specialrule{0em}{5pt}{5pt}
-		(Expr Unary)								
-		&					
-		& 			\\\specialrule{0em}{1pt}{1pt}
-		$\dfrac{\mathcal{P} \vdash A ~~\mathcal{P} \vdash op :: A \rightarrow A ~~\Gamma \vdash x:A}{\mathcal{P},\Gamma \vdash op~x:A}$ 
-		& 
-		&       		\\\specialrule{0em}{5pt}{5pt}
-		(Expr Binary)							
-		&					
-		& 			\\\specialrule{0em}{1pt}{1pt}
-		$\dfrac{\mathcal{P} \vdash A ~~\mathcal{P} \vdash op :: A, A \rightarrow A ~~\Gamma \vdash x_1:A ~~\Gamma \vdash x_2:A}{\mathcal{P},\Gamma \vdash x_1~op~ x_2:A}$ 
-		& 
-		&       		\\\specialrule{0em}{5pt}{5pt}
-%		(Expr +)							
-%		&					
-%		& 			\\\specialrule{0em}{1pt}{1pt}
-%		$\dfrac{\mathcal{P} \vdash + :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1 + x_2:Int}$ 
-%		& 
-%		&       		\\\specialrule{0em}{5pt}{5pt}
-%		(Expr $\times$)							
-%		&					
-%		& 			\\\specialrule{0em}{1pt}{1pt}
-%		$\dfrac{\mathcal{P} \vdash \times :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1 \times x_2:Int}$ 
-%		& 
-%		&       		\\\specialrule{0em}{5pt}{5pt}
-%		(Expr $\div$)							
-%		&					
-%		& 			\\\specialrule{0em}{1pt}{1pt}
-%		$\dfrac{\mathcal{P} \vdash \div :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1 \div x_2:Int}$ 
-%		& 
-%		&       		\\\specialrule{0em}{5pt}{5pt}
-		(Polymorphism)							
-		&					
-		& 			\\\specialrule{0em}{3pt}{3pt}
-		(Poly =)							
-		&					
-		& 			\\\specialrule{0em}{1pt}{1pt}
-		$\dfrac{\mathcal{P} \vdash A ~~\mathcal{P} \vdash = :: A, A \rightarrow Bool ~~\Gamma \vdash x_1:A ~~\Gamma \vdash x_2:A}{\mathcal{P},\Gamma \vdash x_1 = x_2:Bool}$ 
-		& 
-		&       		\\\specialrule{0em}{5pt}{5pt}
-		(Poly $\ne$)							
-		&					
-		& 			\\\specialrule{0em}{1pt}{1pt}
-		$\dfrac{\mathcal{P} \vdash A ~~\mathcal{P} \vdash \ne :: A, A \rightarrow Bool ~~\Gamma \vdash x_1:A ~~\Gamma \vdash x_2:A}{\mathcal{P},\Gamma \vdash x_1 \ne x_2:Bool}$ 
-		& 
-		&       		\\\specialrule{0em}{5pt}{5pt}
-%		(Poly -)							
-%		&					
-%		& 			\\\specialrule{0em}{1pt}{1pt}
-%		$\dfrac{\mathcal{P} \vdash - :: Int \rightarrow Int ~~\Gamma \vdash x:Int}{\mathcal{P},\Gamma \vdash -x:Int}$  
-%		&$\dfrac{\mathcal{P} \vdash - :: Int, Int \rightarrow Int ~~\Gamma \vdash x_1:Int ~~\Gamma \vdash x_2:Int}{\mathcal{P},\Gamma \vdash x_1-x_2:Int}$ 
-%		&       		\\\specialrule{0em}{5pt}{5pt}
-		(Poly $\texttt{FUN}$)							
-		&					
-		& 			\\\specialrule{0em}{1pt}{1pt}
-		$\dfrac{\mathcal{P} \vdash \texttt{FUN} :: A_1,...,A_n \rightarrow A ~~\mathcal{P} \vdash A_1~~...~~\mathcal{P} \vdash A_n ~~\mathcal{P} \vdash A ~~\Gamma \vdash x_1:A_1~~...~~\Gamma \vdash x_n:A_n}{\mathcal{P},\Gamma \vdash \texttt{FUN}(x_1,...,x_n):A}$
-		& 
-		&			\\
-		\specialrule{0em}{5pt}{5pt}\hline
-	\end{tabular}
-\end{table}
+\subsection{Relation}
+User gives the pair of states and the predicates between two open automata for bisimulation checking.
+Relation is the structure created for storing these informations.
+So there would be a list of Relations as the input of checking.
+There are 4 fields in the $Relation$ class storing corresponding information (state1, state2, predicate1, predicate2).
 
-\subsection{Map to SMT-LIB language}
-The pNet semantics can be full translated into SMT-LIB language, though some difference on defining functions exist.
-\begin{table}\caption{\leftline{Mapping}}
-	\begin{tabular}{p{3cm}p{9cm}}
-		\hline\specialrule{0em}{5pt}{5pt}			
-		(Presentation)							
-		&								\\\specialrule{0em}{5pt}{5pt}		
-		&$Sort \lhook\joinrel\longrightarrow$	declare-datatypes				\\\specialrule{0em}{3pt}{3pt}
-		&$Operator \lhook\joinrel\longrightarrow$	declare-function		\\\specialrule{0em}{3pt}{3pt}
-		(Checking)							
-		&								\\\specialrule{0em}{5pt}{5pt}
-		&$dom(\Gamma) \lhook\joinrel\longrightarrow$	declare-const		\\\specialrule{0em}{3pt}{3pt}
-		&$Pred \lhook\joinrel\longrightarrow$	 assert		\\\specialrule{0em}{3pt}{3pt}
-		(Expressions)							
-		&								\\\specialrule{0em}{5pt}{5pt}
-		&$\texttt{FUN}(x_1,...,x_n)$		\\\specialrule{0em}{3pt}{3pt}
-		&$x_1- x_n$  $~~~~~~~\lhook\joinrel\longrightarrow$ declare-function	\\\specialrule{0em}{3pt}{3pt}
-		&$...$	\\\specialrule{0em}{3pt}{3pt}
-		\specialrule{0em}{5pt}{5pt}\hline
-	\end{tabular}
-\end{table}
+\subsection{BisimulationChecker}
+Most of the methods are the same as the $Checker$ module. Except $checkRelation()$ and $checkProofObligation()$.
 
-\section{Submission to Z3}
-\subsection{Z3 Notations}
-Our semantic has already got enough informations for Z3 checking. Z3 has a number of notations for various usages. We only list the notations we needed in our algorithm as follows:
-\TODO{Finish the description.}
-\begin{enumerate}
-\item \texttt{declare-datatypes}
-\item \texttt{declare-function}
-\item \texttt{declare-const}
-\item \texttt{assert}
-\end{enumerate}
+\paragraph{toplevelloop}
+\ERIC{This is currently missing ?} Checking that a given relation is a
+bisimulation means checking for each triple $<s_1,s_2,pred>$ in $\R$,
+for each $OT_1$ in the transitions of $s_1$ leading to a state $s'_1$, it is
+``covered'' by the $\{OT_{2i}$ of $s_2$ that leads to states equivalent to
+$s'_1$ (under assumption $pred$). Here ``covered'' means that the
+disjunction of the predicates in the OTs of $s_2$ implies the
+predicate of $OT_1$, and is realized by:
 
-\subsection{Submission of Algebra}
-Before the submission of the open transitions to Z3, the user-inputed algebra of the pNet should be known at first.
-It gives Z3 informations of the sorts of the expression and the operators, corresponding to the
-\texttt{declare-datatypes} and \texttt{declare-function}.
-We declare the algebra in Z3 logic through Z3 API methods having the same effect as the notations.
-At the same time, we have several internal lists (actually hash maps) \texttt{exprs}, \texttt{funcDecls}, \texttt{sortDatatypes} to store the generated Z3 objects with their names for later proofs.
+\paragraph{checkRelation()} first chooses a open transition $OT_1$
+start at the $state1$. Then collects the open transitions $OT_{2x}$
+start at the $state2$. Collect the $Pred$ and $Assignment$ of the OTs
+at the same time. At Last, invoke $checkProofObligation()$ to check 
+$OT_1$ and the list of collected $OT_{2x}$s.
 
-\subsection{Submission of Open Transitions}
-Each time we submit each open transition to Z3 module, we translate its predicate into Z3 language format and send it for satisfiability checking.
-Every term of the predicate is declared as an \texttt{assert} in Z3.
-A constant action or a parameterized expression is easy to get from the internal list storing the objects while all the variables are not declared at the beginning.
-So we declare them before the submission of a predicate term with the API method conducting \texttt{declare-const}.
+\paragraph{checkProofObligation()} generates the imply formula for bisimulation checking and submit it to Z3.
+The left side of the formula $lhs$ is the conjunction of predicate term and assignments in $OT_1$ (there is no difference with what we do in $Checker$).
+Conjunctions are also generated by the list of collected $OT_{2x}$ one by one.
+The right hand side $rhs$ is the disjunction of these conjunctions.
+Then invoke Z3 method to make a implication relation between $lhs$ and $rhs$.
+But what to check is if there is no case to satisfy the negation of the formula. If solver returns "UNSAT" meaning no case makes implication formula fail, then this relation is proved.
 
-\subsection{Other works}
-\paragraph{Quantifier}
-\paragraph{Filter the State without Precursor}
+\subsection{TODO}
+\begin{itemize}	
+	\item Change the objects attending into the bisimulation checking. Collect the OTs with both given start and target state instead of the start state only.
+	\item Take the predicates into account when generating proof obligation.
+\end{itemize}
 

### 2018-02-05 2018-Arch-pNets/arch-pNets.tex
Couple of minor edits

@@
 allowed in $A(\cB)$ are those belonging to $\Gamma$.  Notice also
-that the restrictions imposed by \defn{archi:application} on the
+that the restrictions imposed by \defn{arch:application} on the
 set of operand components $\cB$ ensure that an interaction in
@@
 \bibliographystyle{abbrv}
-\bibliography{}
+\bibliography{biblio.bib}
 

### 2018-02-06 2016-Weak-FH-Bisim/WeakBisim.tex
Quelques TODOs faciles avant reu

@@
    are open automata where the set
-   of holes are equal %\LUDO{added:} 
-   and of the same sort.  %\LUDO{changed:}
+   of holes are equal 
+   and of the same sort.
 
@@
 Two pNets are FH-bisimilar if there exist a relation between their associated 
-automata that is an FH-bisimulation and their initial states are equivalent.
-\TODO{Ludo: define are equivalent : is in the relation les valeurs des variables des 
-etats initiaux verifient le predicat associe aux etats initiaux}
+automata that is an FH-bisimulation and their initial states are in the relation, i.e. 
+the predicate associated to the relation between the initial states is true.
+\TODO{do we want formulas for this?}
  \end{definition}
@@
 
-\LUDO{added congruence theorem below}
 \begin{theorem}[Congruence]\label{thm-congr-eq}
@@
   equationnal theories for Lotos -- DONE, no answer..., so I got some examples from \cite{Lotos:ISO}}
-
-\TODO{Ludo: ask Simon for weak properties of Bip composition
-  ``operators'' -- DONE!}
 
@@
 	\]
-		with $Q$ ``moving'' \TODO{or is reduced?}, i.e. $J\cap\Holes(Q)\neq\emptyset$ or $I\cap L_Q\neq 
-		\emptyset$.
+		with  $J\cap\Holes(Q)\neq\emptyset$ or $I\cap L_Q\neq 
+		\emptyset$, i.e. $Q$ takes part in the reduction.
 		 Then there exist $v_Q$, $\Pred\,'$, $\Pred\,''$, 

### 2018-02-07 2016-Weak-FH-Bisim/WeakBisim.tex
Reu RAB

@@
 set $I$. Such a family
-is equivalent to the mapping $(i\mapsto a_i)^{i\in I}$.
+is equivalent to the mapping $(i\mapsto a_i)^{i\in I}$, and we will also use mapping 
+notations to manipulate indexed sets.
 To specify the set over which the structure is indexed, 
@@
 the mapping with a single entry $a$ at index $3$; exceptionally, such mappings with
-only a few entries will also be denoted $(3\mapsto a)$. \TODO{We need to define update as $A \uplus \{j \mapsto a\}$ or $A[j \mapsto a]$}
+only a few entries will also be denoted $(3\mapsto a)$.
+%The operation  $A[j \mapsto a]$ updates the value associated to $j$ in map $A$ so that 
+%it 
+%now corresponds to $a$. 
 When this is not ambiguous, we shall use abusive vocabulary and
@@
 
-Let $\uplus$ be the disjoint union operator on indexed sets. 
+$\uplus$ is the disjoint operator on sets. We extend it to  disjoint union  of indexed 
+sets defined by the merge of the 
+two sets provided they are indexed on disjoint families.
 The elements
-of the union are then accessed by using an index of one of the two
+of the union of two indexed sets are then accessed by using an index of one of the two
 joined families.
@@
 \label{section:pnets}
-
-\ERIC{Keep minimum defs here too be independent from FORTE}
 
@@
 \Holes(\mylangle \pNet_i^{i\in I}\!,\Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) 
-=J\cup{\displaystyle \bigcup_{i\in 
+=J\uplus{\displaystyle \bigcup_{i\in 
 I}\Holes(\pNet_i)}\\
@@
 \item
-The set of leaves of a pNet is the set of all pLTSs occurring in the structure, defined inductively as:
+The set of leaves of a pNet is the set of all pLTSs occurring in the structure, defined 
+inductively as:
+\TODO{Not very nice but at least of the right kind for the definition of composition}
 \[\begin{array}{l}
-\Leaves(\mylangle S,s_0, \to\myrangle) \!=\! \{ \mylangle S,s_0, \to\myrangle \}\\
+\Leaves(\mylangle S,s_0, \to\myrangle) \!=\!\emptyset\\
 \Leaves(\mylangle \pNet_i^{i\in I}\!,%Sort_j^{j\in J}
-\overline{\Sort}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \bigcup_{i\in 
-I}\Leaves(\pNet_i)}
+\overline{\Sort}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \biguplus_{i\in 
+I}\Leaves(\pNet_i)\uplus\{i\mapsto \pNet_i|\pNet_i=\mylangle S,s_0, \to\myrangle\}}
 \end{array}\]
@@
   \triangleright| \forall i\in L. s_i \in S_i\}$.
+\TODO{this definition is not valid because L is undefined and leaves only exist for pNets 
+-> REMOVE? this would mean that a pNet is not a pLTS ...}
 A pLTS being its own single leave:
@@
 
-\RAB{Exemple  Fig3 a revoir: Les regles ne passent... }
-
 Note that while the scenario above is expressed as a single
@@
 \end{definition}
-\TODO{$\uplus\{j_0\mapsto \pNet'\}$ non defini}
 
@@
 automata that is an Weak FH-bisimulation and their initial states are equivalent.
-\TODO{define equivalent}
+\TODO{LUDO: define equivalent}
  \end{definition}
@@
 \TODO{Here we should include:
-  \\  - A definition for Weak FH-Bisimulation
   \\  - A sufficient condition for an open PNet to preserve Weak-FH,
@@
 }
-
-\TODO{Eric: ask Elie, Hubert or others about interesting weak
-  equationnal theories for Lotos -- DONE, no answer..., so I got some examples from \cite{Lotos:ISO}}
 
@@
  $\mathcal{R}$ that is an FH-bisimulation between the open automata of the two pNets. 
- We will consider the relation $\mathcal{R}'=\{(s,t|\Pred_{s,t})|s=s'\uplus s'' \land 
- t=t'\uplus s'' \land s''\in \mathcal{S}_P \land (s',t'|\Pred_{s,t})\in\mathcal{R}\}$ \TODO{$\uplus$ entre states?} 
+ We will consider the relation\footnote{$\uplus$ is defined on sets as the disjoint union 
+ of the contained indexed 
+ sets} $\mathcal{R}'=\{(s,t|\Pred_{s,t})|s=s'\uplus s'' \land 
+ t=t'\uplus s'' \land s''\in \mathcal{S}_P \land (s',t'|\Pred_{s,t})\in\mathcal{R}\}$
+
  where $\mathcal{S}_S$ is the set of states of the open automaton of $P$.	We will prove 

### 2018-02-07 2018-Arch-pNets/arch-pNets.tex
Another minor
definition open pnets

@@
 %% \usepackage[disable,colorinlistoftodos,bordercolor=white]{todonotes}
+\usepackage{macrospNets}
 
@@
 \newcommand{\todoSBin}[2][inline,color=green!40]{\todo[#1]{\textbf{To-do Simon: } {#2}}}
+\newcommand{\Ludo}{\\\hfill\mdash Ludo}
+\newcommand{\noteLH}[2][color=green!40, size=\tiny]{\todo[#1]{{#2}\Ludo}}
+\newcommand{\noteLHin}[2][inline,color=green!40]{\todo[#1]{{#2}\Ludo}}
+\newcommand{\todoLH}[2][color=green!40, size=\tiny]{\todo[#1]{\textbf{To-do Ludo:} {#2}}}
+\newcommand{\todoLHin}[2][inline,color=green!40]{\todo[#1]{\textbf{To-do Ludo: } {#2}}}
 
@@
 
-%***********************************************************
-%***********************************************************
+%****************************************************************
+%****************************************************************
 
@@
 
-%***********************************************************
+%****************************************************************
 
@@
 
-%***********************************************************
+%****************************************************************
 \subsection{Architectures}
@@
 
-%***********************************************************
-%***********************************************************
+pNets are tree-like structures, where the leaves are either
+\emph{parameterised labelled transition systems (pLTSs)}, expressing the
+behaviour of basic processes, or \emph{holes}, used as placeholders
+for unknown processes, of which we only specify the set of possible
+actions, this set is named the \emph{sort}.
+Nodes of the tree (pNet nodes) are synchronising artifacts, using a
+set of \emph{synchronisation vectors} that express the possible
+synchronisation between the parameterised actions of a subset of the
+sub-trees.
+
+%\smallskip\noindent
+\paragraph*{Notations.}
+We extensively use indexed structures
+over some countable indexed sets, which are equivalent to mappings over
+the countable set. % . The indexes will usually be
+% integers, bounded or not. Such an indexed family is
+%denoted
+%follows:
+$a_i^{i\in I}$
+%, or equivalently  $(i\mapsto a_i)^{i\in I}$
+denotes a family of elements $a_i$ indexed over the
+set $I$. % Such a family
+% is equivalent to the mapping $(i\mapsto a_i)^{i\in I}$.
+% To specify the set over which the structure is indexed,
+% indexed structures are always denoted with an exponent of the form $i\in I$
+% (arithmetic only appears in the indexes if necessary).
+$a_i^{i\in I}$ defines both $I$ the set over which the family is
+indexed (called \emph{range}), and $a_i$ the elements of the family.
+E.g., $a^{i\in\{3\}}$ is the mapping with a single entry $a$ at index
+$3$ ; abbreviated $(3\mapsto a)$ in the following.
+When this is not
+ambiguous, we shall use notations for sets, and typically write
+``indexed set over I'' when formally we should speak of multisets, and
+write $x\in a_i^{i\in I}$ to mean $\exists i\in I.\, x=a_i$.  An empty
+family is denoted $\emptyset$. We
+denote classically with an overline -- $\overline{a}$  -- a family when the indexing set 
+is
+not meaningful.  $\uplus$ is the disjoint union on
+indexed sets.
+
+\paragraph*{Term algebra.}
+Our models rely on a notion of parameterised actions, that are
+symbolic expressions using data types and variables. As our model aims
+at encoding the low-level behaviour of possibly very different
+programming languages, we do not want to impose one specific algebra
+for denoting actions, nor any specific communication mechanism. So we
+leave unspecified the constructors of the algebra that will allow building
+expressions and actions. Moreover, we use a generic {\em action interaction}
+mechanism, based on (some sort of) unification between two or more action
+expressions, to express various kinds of communication or
+synchronisation mechanisms.
+
+\def\Talg{\mathcal{T}_{\Sigma,\P}}
+Formally, we assume the existence of a term algebra $\Talg$,
+where $\Sigma$ is the signature of the data and action constructors,
+and $\P$ a set of variables. Within $\Talg$, we distinguish a set of
+data expressions $\mathcal{E}_\P$, including a set of boolean
+expressions $\mathcal{B}_{\P}$ ($\mathcal{B}_{\P}\subseteq\mathcal{E}_\P$).
+On top of $\mathcal{E}_\P$ we build the action algebra
+$\mathcal{A}_\P$, with $\mathcal{A}_P\subseteq\mathcal{T}_\P,
+\mathcal{E}_P\cap\mathcal{A}_P=\emptyset$;
+naturally action terms will use data expressions as subterms.
+To be able to reason about the data flow between pLTSs, we
+distinguish \emph{input variables} of the form $?x$ within terms; the function
+$\vars(t)$ identifies the set of variables in a term
+$t\in\AlgT$, and $iv(t)$ returns its input variables.
+
+pNets can encode naturally the notion of input actions in value-passing CCS
+\cite{Milner89} or of usual point-to-point message passing calculi, but it also allows
+for more general mechanisms, like gate negociation in Lotos, or broadcast
+communications. Using our notations, value-passing actions \emph{\`a la} CCS would be
+encoded as $a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs (in which $v_i$ are 
+action terms containing no input variables). 
+%For Lotos-style
+%distributed synchronisation, we use synchronisation vectors that encode matching data
+%offers on a common gate; or 
+We can also use more complex action structure such as Meije-SCCS action
+monoids, like in $a.b$, $a^{f(n)}$ (see \cite{deSimone85}). The expressiveness of the 
+synchronisation constructs
+will depend on the action algebra.
+
+\subsection{The (open) pNets Core Model}
+\label{section:pNets}
+
+A pLTS is a labelled transition system with variables; variables can be
+manipulated, defined, or accessed inside states, actions, guards, and
+assignments. Without loss of generality and to simplify the formalisation, we suppose 
+here that 
+variables are local to each 
+state: each state has its set of variables disjoint from the others. Transmitting 
+variable values from one state to the other can be done by explicit assignment. 
+%Similarly, to simplify the management of variables and without loss of expressivity, we 
+%suppose that transitions looping to the same state does not do assignments.
+Note that we make no assumption on finiteness of the set of states nor
+on finite branching of the transition relation.
+
+We first define the set of actions a pLTS can use, let $a$
+range over action labels, $\symb{op}$ are operators, and $x_i$ range over
+variable names. Action terms are:
+\[
+\begin{array}[l]{rcl@{\quad}p{5.5cm}}
+  \alpha\in\AlgA&::=&a(p_1,\ldots,p_n)&\text{action terms}\\
+  p_i&::=& ?x~|~\symb{Expr}&\text{parameters (input variable or expression)}\\
+  \symb{Expr}&::=& 
+  \symb{Value}~|~x~|~\symb{op}(\symb{Expr}_1,..,\symb{Expr}_n)&\text{Expressions}
+\end{array}
+\]
+The input variables in an action term are those marked with a
+$\symb{?}$.
+We additionally suppose that each input variable does not
+appear somewhere else in the same action term:
+$p_i=?x\Rightarrow\forall j\neq i.\, x\notin \vars(p_j)$
+
+\begin{definition}[pLTS]
+\label{pLTS}
+A pLTS is a tuple
+$\pLTS\triangleq\mylangle S,s_0, \to\myrangle$ where:
+\begin{itemize}
+\item[$\bullet$]
+$S$ is a set of states.
+\item[$\bullet$]
+$s_0 \in S$ is the initial state.
+%\item[$\bullet$]
+ %Variables in
+%$\iv(\alpha)$ are assigned by the action, other variables can be assigned
+%by the additional assignments.
+\item[$\bullet$] $\to \subseteq S \times L \times S$ is the transition relation and 
+$L$ is the set of labels of the form
+$\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in J}\rangle$,
+where $\alpha \in\AlgA$ is a parameterised action, $e_b \in
+\AlgB$ is a guard, and the variables $x_j\in P$
+are assigned the expressions $e_j\in \AlgE$.
+If 
+$s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
+		J}\rangle} s'\in \to $ then $\iv(\alpha)\!\subseteq\! \vars(s')$, 
+		$\vars(\alpha)\backslash \iv(\alpha)\!\subseteq\! \vars(s)$, 
+		$\vars(e_b)\!\subseteq\! \vars(s')$, and
+		$\forall j\!\in\! J .\,\vars(e_j)\!\subseteq\! \vars(s)\land 
+		x_j\!\in\!\vars(s')$. %,  and $s= s'\Rightarrow J=\emptyset$.
+
+\end{itemize}
+\end{definition}
+
+Now we define
+pNet nodes, as constructors for hierarchical behavioural structures.
+A pNet has a set of sub-pNets that can be either pNets or pLTSs, and a
+set of Holes, playing the role of process parameters.
+
+A composite pNet consists of a set of sub-pNets exposing
+a set of actions, each of them triggering internal actions in each of
+the sub-pNets. The synchronisation between global actions and
+internal actions is given by  \emph{synchronisation vectors}: a
+synchronisation vector synchronises one or several internal actions, and
+exposes a single resulting global action.
+Actions involved at the pNet level (in the synchronisation vectors) do
+not need to distinguish between input and output
+variables. Action terms for pNets are defined as follows:
+\[\begin{array}[l]{rcl@{\quad}l}
+  \alpha\in \AlgAS &::=&a(Expr_1,\ldots,Expr_n)
+\end{array}
+\]
+
+\begin{definition}[pNets]\label{def-pnets}
+A pNet is a hierarchical structure where leaves are pLTSs and holes:\\
+$\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in 
+K}\myrangle$
+where
+\begin{itemize}
+\item[$\bullet$] $I \in \I$ is the set over which sub-pNets are indexed.
+\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets.
+%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which 
+%sub-pNets are indexed.
+
+\item[$\bullet$] $J\!\in\!\I_\P$ is a set of indexes, called \emph{holes}.
+$I$ and $J$ are \emph{disjoint}: $I\!\cap\! J=\emptyset$,  $I\!\cup\! J\neq\emptyset$
+\item[$\bullet$] $\Sort_j \subseteq \AlgAS$ is a set of action terms, denoting the 
+\emph{sort} of
+hole $j$.
+
+\item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
+  synchronisation vectors ($K\in\I_\P$). $\forall k\!\in\! K,
+  \symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k$ where
+  $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
+  $\forall i\!\in\!
+  I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$,  $\forall j\!\in\!
+  J_k.\,\alpha_{j}\!\in\!\Sort_j$, and $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
+  J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
+$\Label(\symb{SV}_k) = \alpha'_k$.
+
+\end{itemize}
+\end{definition}
+
+The preceding definition relies on the auxiliary functions below:
+
+\begin{definition}[Sorts, Holes, Leaves of pNets]
+  \begin{itemize}
+  \item The sort of a pNet is its signature, i.e. the set of actions it can
+perform. In the definition of sorts, we do not need to distinguish
+input variables (that specify the dataflow within LTSs), so for
+computing LTS sorts, we use a substitution operator\footnote{$\subst{y_k\gets x_k}^{k\in 
+K}$ is the parallel substitution 
+operation.} to remove the
+\emph{input marker} of variables. Formally:
+\[
+\begin{array}{l}
+\Sortop(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{x \gets ?x| 
+x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
+    J}\rangle} s'\in \to \} \\
+\Sortop(\mylangle \overline{\pNet}\!, %\pNet_i^{i\in I}, \Sort_j^{j\in J}
+\overline{\pNet}\!,
+\overline{\symb{SV}}\myrangle)
+=\{\alpha' |\, \overline{\alpha}%\alpha_j^{j\in J_k}
+\to\alpha'\in\set{\symb{SV}}\}
+\end{array}
+\]
+
+\item
+The set of holes of a pNet is defined inductively; the sets of holes
+in a pNet node and its subnets are all disjoint:
+  \[\begin{array}{l}
+\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset \\
+\Holes(\mylangle \pNet_i^{i\in I}\!,\Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) 
+=J\uplus{\displaystyle \bigcup_{i\in 
+I}\Holes(\pNet_i)}\\
+\forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
+\forall i_1,i_2\in I.\,i_1\neq i_2\Rightarrow  
+\Holes(\pNet_{i_1})\cap\Holes(\pNet_{i_2})=\emptyset
+\end{array}\]
+\item
+The set of leaves of a pNet is the set of all pLTSs occurring in the structure, defined 
+inductively as:
+\noteLH{Not very nice but at least of the right kind for the definition of composition}
+\[\begin{array}{l}
+\Leaves(\mylangle S,s_0, \to\myrangle) \!=\!\emptyset\\
+\Leaves(\mylangle \pNet_i^{i\in I}\!,%Sort_j^{j\in J}
+\overline{\Sort}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \biguplus_{i\in 
+I}\Leaves(\pNet_i)\uplus\{i\mapsto \pNet_i|\pNet_i=\mylangle S,s_0, \to\myrangle\}}
+\end{array}\]
+\end{itemize}
+\end{definition}
+
+A pNet $Q$ is \emph{closed} if it has no hole: $\Holes(Q)=\emptyset$; else it
+is said to be \emph{open}.
+
+%****************************************************************
+%****************************************************************
 

### 2018-02-08 2018-Arch-pNets/arch-pNets.tex
Added the architecture composition

@@
 \usepackage{amsmath,amsthm,amscd}
-\usepackage{amssymb}  %for blackboard B
-\usepackage{rotating} %to rotate the figures
+\usepackage{amssymb}    % for blackboard B
+\usepackage{rotating}   % to rotate the figures
 \usepackage{mathpartir} % math paragraph + inference rules
+\usepackage{mathtools}  % for align, multline etc.
 \usepackage{caption}
@@
 \newcommand{\IMextend}[2]{\ensuremath{#1 \ltimes #2}}
+\newcommand{\arcomp}{\oplus}
+\newcommand{\Arcomp}{\Bigoplus}
+\newcommand{\expmix}{\oplus}
 
@@
   \label{defn:arch:composition}
+  Let $A_i = (\cC_i, P_{A_i}, V_{A_i}, \Gamma_i)$, for $i = 1,2$,
+  be two architectures.  The \emph{composition} of $A_1$ and
+  $A_2$ is the architecture $A_1 \arcomp A_2 = (\cC_1 \cup \cC_2,
+  P_{A_1} \cup P_{A_2}, V_{A_1} \cup V_{A_2}, \Gamma)$, where
+%
+  \begin{equation}
+    \label{eq:arch:composition}
+    \Gamma = \setdefb{
+      (a, g_1 \land g_2, e_1 \expmix e_2) 
+    }{
+      (a \cap P_{A_i}, g_i, e_i) \in \Gamma_i,
+      \text{ for } i = 1,2
+    }
+    \,.
+  \end{equation}
+\end{definition}
 
-\end{definition}
+\begin{proposition}[Properties of $\arcomp$]
+  \label{prop:arcomp:nice}
+  Architecture composition $\arcomp$ is commutative and
+  associative; it is idempotent if all coordinating components
+  are deterministic; $A_{id} = \bigl(\emptyset, \emptyset,
+  \emptyset, \{\emptyset\}\bigr)$ is its neutral element, \ie for
+  any architecture $A$, we have $A \oplus A_{id} = A$.
+  Furthermore, for any component $B$, we have $A_{id}(B) = B$.
+  %PCA: replaced ``holds'' by ``we have''
+\end{proposition}
+%
+\begin{proof}[Sketch of the proof]
+  Commutativity and associativity follow from the corresponding
+  properties of set union, Boolean conjunction and
+  \todoSB{Check ``semi''}\hl{semilattice meet}.
+%
+  Suppose we have two architectures $A = A'$.  This does not
+  necessarily mean that their sets of coordinating components
+  coincide.  However, if all the involved coordinating components
+  are deterministic, then, in any state of $(A \arcomp A')(\cB)$,
+  both architectures will impose the same restrictions, enabling
+  the same interactions between the coordinating and operand
+  components.  Hence, we have $(A \arcomp A')(\cB) = A(\cB) =
+  A'(\cB)$.  Since this holds for any set of components $\cB$, we
+  conclude that $A \arcomp A' = A = A'$.
+%
+  The properties of $A_{id}$ follow immediately from the
+  definitions of architecture application and composition.
+\end{proof}
+
+%****************************************************************
+\subsection{Preservation of safety properties}
+\label{secn:safety}
 

### 2018-02-09 2016-Weak-FH-Bisim/WeakBisim.tex
definition open pnets
Guard and eric's changes in weak bisim and archi

@@
 \usepackage{macrospNets}
-
-\def\AlgT{\mathcal{T}}
-\def\AlgE{\mathcal{E}}
-\def\AlgA{\mathcal{A}}
-\def\AlgAS{\mathcal{A}_S}
-\def\AlgB{\mathcal{B}}
-\def\AlgI{\mathcal{I}}
 
@@
 $t\in\AlgT$, and $iv(t)$ returns its input variables.
-
-pNets can encode naturally the notion of input actions in value-passing CCS
-\cite{Milner89} or of usual point-to-point message passing calculi, but it also allows
+Action algebras can encode naturally usual point-to-point message passing calculi (using 
+$a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs), but it also allows
 for more general mechanisms, like gate negociation in Lotos, or broadcast
-communications. Using our notations, value-passing actions \emph{\`a la} CCS would be
-encoded as $a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs (in which $v_i$ are 
-action terms containing no input variables). 
-%For Lotos-style
-%distributed synchronisation, we use synchronisation vectors that encode matching data
-%offers on a common gate; or 
-We can also use more complex action structure such as Meije-SCCS action
-monoids, like in $a.b$, $a^{f(n)}$ (see \cite{deSimone85}). The expressiveness of the synchronisation constructs
-will depend on the action algebra.
+communications.
 
@@
 $s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
-		J}\rangle} s'\in \to $ then $\iv(\alpha)\!\subseteq\! \vars(s')$, 
+		J}\rangle} s'\in \to $ then 
+% REMOVED BECAUSE USELESS: $\iv(\alpha)\!\subseteq\! \vars(s')$, 
 		$\vars(\alpha)\backslash \iv(\alpha)\!\subseteq\! \vars(s)$, 
-		$\vars(e_b)\!\subseteq\! \vars(s')$, and
-		$\forall j\!\in\! J .\,\vars(e_j)\!\subseteq\! \vars(s)\land 
+		$\vars(e_b)\!\subseteq\! \vars(s)\cup\varsigma(\alpha)$, and
+		$\forall j\!\in\! J .\,\vars(e_j)\!\subseteq\! \vars(s)\cup\varsigma(\alpha)\land 
 		x_j\!\in\!\vars(s')$. %,  and $s= s'\Rightarrow J=\emptyset$. 
-
 \end{itemize}
@@
 A composite pNet consists of a set of sub-pNets exposing
-a set of actions, each of them triggering internal actions in each of
+a set of actions, each of them synchronising actions in each of
 the sub-pNets. The synchronisation between global actions and
@@
 Actions involved at the pNet level (in the synchronisation vectors) do
-not need to distinguish between input and output
+not need to distinguish  input 
 variables. Action terms for pNets are defined as follows:
@@
   synchronisation vectors ($K\in\I_\P$). $\forall k\!\in\! K,
-  \symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k$ where
+  \symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k\,|\,g_k$ where
   $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
@@
   J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
-$\Label(\symb{SV}_k) = \alpha'_k$.
+$\Label(\symb{SV}_k) = \alpha'_k$. $g_k \in \AlgB$ is a guard associated to the vector 
+$\vars(g_k)\subseteq \bigcup_{l\in I_k\uplus J_k}{\vars({\alpha_l})}$.
 

### 2018-02-09 2018-Arch-pNets/arch-pNets.tex
commit
Guard and eric's changes in weak bisim and archi

@@
     \emptyset}$ the \emph{support} of the interaction $a$.
+\noteLH{why not introduce supp earlier and use it for $V_a$?}
   %% We call the set of ports $P$ the \emph{domain} of the
@@
 $t\in\AlgT$, and $iv(t)$ returns its input variables.
-
-pNets can encode naturally the notion of input actions in value-passing CCS
-\cite{Milner89} or of usual point-to-point message passing calculi, but it also allows
+Action algebras can encode naturally usual point-to-point message passing calculi (using 
+$a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs), but it also allows
 for more general mechanisms, like gate negociation in Lotos, or broadcast
-communications. Using our notations, value-passing actions \emph{\`a la} CCS would be
-encoded as $a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs (in which $v_i$ are 
-action terms containing no input variables). 
-%For Lotos-style
-%distributed synchronisation, we use synchronisation vectors that encode matching data
-%offers on a common gate; or 
-We can also use more complex action structure such as Meije-SCCS action
-monoids, like in $a.b$, $a^{f(n)}$ (see \cite{deSimone85}). The expressiveness of the 
-synchronisation constructs
-will depend on the action algebra.
+communications.
 
@@
 $s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
-		J}\rangle} s'\in \to $ then $\iv(\alpha)\!\subseteq\! \vars(s')$, 
+		J}\rangle} s'\in \to $ then 
+% REMOVED BECAUSE USELESS: $\iv(\alpha)\!\subseteq\! \vars(s')$, 
 		$\vars(\alpha)\backslash \iv(\alpha)\!\subseteq\! \vars(s)$, 
-		$\vars(e_b)\!\subseteq\! \vars(s')$, and
-		$\forall j\!\in\! J .\,\vars(e_j)\!\subseteq\! \vars(s)\land 
+		$\vars(e_b)\!\subseteq\! \vars(s)\cup\varsigma(\alpha)$, and
+		$\forall j\!\in\! J .\,\vars(e_j)\!\subseteq\! \vars(s)\cup\varsigma(\alpha)\land 
 		x_j\!\in\!\vars(s')$. %,  and $s= s'\Rightarrow J=\emptyset$.

### 2018-02-09 2016-Weak-FH-Bisim/WeakBisim.tex
essai magical op ...
OOps mistake inhole def

@@
 sub-trees.
+
+\LUDO{introduce magic op}
+$\CreateISet{a}{i}$ creates a single entry indexed set $(i\mapsto a)$ \emph{but only if 
+$a$ is not already an indexed set.}
 
@@
   \[\begin{array}{l}
-\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset \\
+\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset\\
 \Holes(\mylangle \pNet_i^{i\in I}\!,\Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) 
@@
 inductively as:
-\TODO{Not very nice but at least of the right kind for the definition of composition}
+\TODO{Nicer here at least}
 \[\begin{array}{l}
-\Leaves(\mylangle S,s_0, \to\myrangle) \!=\!\emptyset\\
+\Leaves(\mylangle S,s_0, \to\myrangle) \!=\!\mylangle S,s_0, \to\myrangle\\
 \Leaves(\mylangle \pNet_i^{i\in I}\!,%Sort_j^{j\in J}
 \overline{\Sort}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \biguplus_{i\in 
-I}\Leaves(\pNet_i)\uplus\{i\mapsto \pNet_i|\pNet_i=\mylangle S,s_0, \to\myrangle\}}
+I}\CreateISet{\Leaves(\pNet_i)}{i} }
 \end{array}\]
@@
 			\inferrule*[myfraction=\reddottedrule]
-			{\{s \xrightarrow{\alpha}_p s'\} ,\emptyset ,
+			{\{s \xrightarrow{\alpha} s'\} ,\emptyset ,
 			e_b,\left\{x_j\gets e_j\right\}^{j\in J}}
@@
 		}
-		$
+		$\LUDO {removed a ${}_p$ that was not bound}
 	\end{description}
@@
 	synchronisation vector.
-
+	\LUDO{now with the magical operator ... $s_m$ and $s_m'$ are a bit ill-typed terms. 
+	Not very happy of the new rule}
 	\begin{description}
@@
     	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
-    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
-    		\ostate{(s_i^\prime)^{i\in L_m}}}
+    	{\ostate{s_m} \OTarrow {v_m}
+    		\ostate{s_m'}}
     	%\land
     	%Leaves(\pNet_m) = \overline{\pLTS}^{L_k})
-    	\\
+    	\\\forall m\in I_k. \CreateISet{s_m}{i}=s_{i}^{i \in L_m} \\
+		\forall m\in I_k. \CreateISet{s_m'}{i}=(s_i^\prime)^{i\in L_m} \\
     	I' = \biguplus_{m\in I_k}\!\! I_m'

### 2018-02-09 2018-Arch-pNets/arch-pNets.tex
Avant tentative d uniformisation notations

@@
   and valuations.}
+
+\todoLHin{proposed notations:}
+$g$ are boolean expressions
+$e_i$ are updates/assignments
+
+\todoLHin{Remove term algebra or simplify?}
+\todoLHin{universal domain $\implies$ remove sort}
+\todoLHin{replace assignments by $e_i$}
+
+In Archi we have a whereas in pnets we have $\alpha$ where, approximately $\alpha = 
+a(x_1..x_n)$ except that a is port name in archi and action name in pnets.
+Is this true? can we unify better? or is it sufficient?
 
@@
 \label{secn:pNets}
-
+\todoLHin{rewrite after uniformisation}
 pNets are tree-like structures, where the leaves are either
@@
 data expressions $\mathcal{E}_\P$, including a set of boolean
-expressions $\mathcal{B}_{\P}$ ($\mathcal{B}_{\P}\subseteq\mathcal{E}_\P$).
+expressions \todoLHin{$\mathcal{B} \to g$}
+$\mathcal{B}_{\P}$ ($\mathcal{B}_{\P}\subseteq\mathcal{E}_\P$).
 On top of $\mathcal{E}_\P$ we build the action algebra
@@
 range over action labels, $\symb{op}$ are operators, and $x_i$ range over
-variable names. Action terms are:
+variable names. Action terms are:\noteLH{Eric suggests to remove this: too precise. I 
+think last Expression should be removed not sure about the rest -- to be discussed}
 \[
@@
 $L$ is the set of labels of the form
+
 $\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in J}\rangle$,

### 2018-02-09 2018-Arch-pNets/arch-pNets.tex
unification trial ...

@@
 
+\paragraph{Unifying notations -- remarks}
+
 \todoLHin{proposed notations:}
@@
 Is this true? can we unify better? or is it sufficient?
+
+states looks ok, but initial state is $s_0$ in pnet and not in archi : $s^0$ . exponent 
+position was removed from pnet because we found it complex with indexed set notation but 
+could be ok.
 
@@
 
-$\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in J}\rangle$,
-where $\alpha \in\AlgA$ is a parameterised action, $e_b \in
-\AlgB$ is a guard, and the variables $x_j\in P$
-are assigned the expressions $e_j\in \AlgE$.
+$\langle \alpha,~g,~e\rangle$,
+where $\alpha \in\AlgA$ is a parameterised action, $g$ is a guard, and the variables 
+$x_j\in \vars(s')$
+are assigned the updates in $e$.
 If 
-$s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
-		J}\rangle} s'\in \to $ then 
+$s \xrightarrow{\langle \alpha,~g,~e\rangle} s'\in \to $ then 
 % REMOVED BECAUSE USELESS: $\iv(\alpha)\!\subseteq\! \vars(s')$, 
 		$\vars(\alpha)\backslash \iv(\alpha)\!\subseteq\! \vars(s)$, 
-		$\vars(e_b)\!\subseteq\! \vars(s)\cup\varsigma(\alpha)$, and
-		$\forall j\!\in\! J .\,\vars(e_j)\!\subseteq\! \vars(s)\cup\varsigma(\alpha)\land 
-		x_j\!\in\!\vars(s')$. %,  and $s= s'\Rightarrow J=\emptyset$.
+		$\vars(g)\!\subseteq\! \vars(s)\cup\vars(\alpha)$, and
+		$\vars(\codom(e))\!\subseteq\! \vars(s)\cup\vars(\alpha)\land 
+		\vars(\dom(e))\!\in\!\vars(s')$. %,  and $s= s'\Rightarrow J=\emptyset$.
 
@@
 \end{definition}
-
+\noteLH[]{}is dom and codom clear?
 Now we define
@@
 A pNet is a hierarchical structure where leaves are pLTSs and holes:\\
-$\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in 
+$\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, J, \symb{SV}_k^{k\in 
 K}\myrangle$
@@
 $I$ and $J$ are \emph{disjoint}: $I\!\cap\! J=\emptyset$,  $I\!\cup\! J\neq\emptyset$
-\item[$\bullet$] $\Sort_j \subseteq \AlgAS$ is a set of action terms, denoting the 
-\emph{sort} of
-hole $j$.
+%\item[$\bullet$] $\Sort_j \subseteq \AlgAS$ is a set of action terms, denoting the 
+%\emph{sort} of
+%hole $j$.
 
@@
   J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
-$\Label(\symb{SV}_k) = \alpha'_k$. $g_k \in \AlgB$ is a guard associated to the vector 
+$\Label(\symb{SV}_k) = \alpha'_k$. $g_k $ is a guard associated to the vector 
 $\vars(g_k)\subseteq \bigcup_{l\in I_k\uplus J_k}{\vars({\alpha_l})}$.

### 2018-02-11 2018-Arch-pNets/arch-pNets.tex
Added compositionality of safety properties *with proof*

--- 2018-02-09 2018-Arch-pNets/arch-pNets.tex
@@
 \newcommand{\false}{\ensuremath{\mathtt{f\!f}}}
-\newcommand{\noop} {\ensuremath{\mathsf{skip}}}
+\newcommand{\noop} {\ensuremath{\emptyset}} % \mathsf{skip}
 
@@
 \newcommand{\val}[3][]{%
-  \ensuremath{\sigma^{#2}_{#3}%
-    \ifthenelse{\isempty{#1}}{}{(#1)}%
-  }%
+  \ensuremath{#1{\sigma}^{#2}_{#3}}%
 }
-%% \DeclareMathOperator{\supp}{supp}
+\newcommand{\primeit}[1]{#1'}
+\newcommand{\doubleprimeit}[1]{#1''}
+
+\newcommand{\export}[1][]{\ensuremath{\varepsilon_{#1}}}
+\newcommand{\valdiff}[2]{\ensuremath{#1 \triangle #2}}
 \newcommand{\supp}[1]{\ensuremath{\mathrm{supp}(#1)}}
@@
 \newcommand{\arcomp}{\oplus}
+\newcommand{\arequiv}{\equiv}
 \newcommand{\Arcomp}{\Bigoplus}
-\newcommand{\expmix}{\oplus}
+\newcommand{\expmix}{\wedge}
+\newcommand{\order}{\leqslant}
+
+\makeatletter
+\newcommand{\doubletilde}[1]{{%
+  \mathpalette\double@tilde{#1}%
+}}
+\newcommand{\double@tilde}[2]{%
+  \sbox\z@{$\m@th#1\tilde{#2}$}%
+  \ht\z@=.9\ht\z@
+  \tilde{\box\z@}%
+}
+\makeatother
+
+\newcounter{tempctr}
+\newcommand{\breakenumistart}{%
+  \setcounter{tempctr}{\value{enumi}}%
+  \end{enumerate}%
+}
+\newcommand{\breakenumiend}{%
+  \begin{enumerate}%
+  \setcounter{enumi}{\value{tempctr}}%
+}
 
@@
 \todoSBin{Preliminaries on the universal(?) data domain $\data$
-  and valuations.}
+  and valuations.
+
+For two valuations $\val{1}{}, \val{2}{} : V \rightarrow \data$,
+we denote \[\valdiff{\val{1}{}}{\val{2}{}} \bydef{=} \setdefb{v
+  \in V}{\val{1}{}(v) \neq \val{2}{}(v)}\] the set of variables
+that are assigned different values by the two valuations.
+
+To guarantee preservation of properties guards and expressions
+have to be \emph{monotonic}.  In the case of a trivial order, \ie
+when nothing is comparable, \emph{any guard or expression is
+  monotonic}.  Thus, this is not really a constraint!
+}
 
@@
   \label{defn:component}
-  A \emph{component} is a tuple $(Q, q^0, P, V, \val{0}{},
-  \goesto{})$, where
+  A \emph{component} is a tuple $(Q, q^0, V, \val{0}{}, P,
+  \export{}, \goesto{})$, where
   \begin{itemize}
@@
     \emph{initial state}, 
-  \item $P$ is a set of \emph{ports},
   \item $V$ is a set of \emph{component variables},
@@
     valuation} of the component variables, 
+  \item $P$ is a set of \emph{ports}, with
+    \noteSB{Added this}\hl{$\export : P \rightarrow 2^V$ 
+    the \emph{export function},}
   \item $\goesto{}\, \subseteq
@@
     labelled by triples consisting of an \emph{interaction}
-    $a \subseteq P$, a Boolean \emph{guard} $g \in
+    $\emptyset \neq a \subseteq P$, a Boolean \emph{guard} $g \in
     \guards{V}$ and an \emph{update expression} $e \in
@@
 %
-  We call the pair of sets $(P,V)$ the \emph{interface} of the
+  We call \noteSB{Maybe rather $(P, \export)$}\hl{the pair of sets $(V,P)$} the \emph{interface} of the
   component.\,\footnote{%
@@
 %
-  Notations $q \goesto{a} q'$, $q \goesto{a}$ and $q
-  \notgoesto{a}$ are as usual; for a component $B$, we denote
-  $Q_B$, $q^0_B$, $P_B$, $V_B$, $\val{0}{B}$ and $\goesto[B]{}$
-  the constituents of $B$.
+  Notations $q \goesto{a} q'$ and $q \goesto{a}$ are as usual;
+  for a component $B$, we denote $Q_B$, $q^0_B$, $P_B$, $V_B$ and
+  $\val{0}{B}$ the corresponding constituents of $B$.  We will
+  skip the index on the transition relations $\goesto{}$, since it
+  is always clear from the context.
 \end{definition}
@@
   \label{defn:comp:semantics}
-  The \emph{open semantics} of a component $B = (Q, q^0, P, V,
-  \val{0}{}, \goesto{})$ is given by the LTS $\semopen{B} = (S,
+  The \emph{open semantics} of a component $B = (Q, q^0, V,
+  \val{0}{}, P, \export, \goesto{})$ is given by the LTS $\semopen{B} = (S,
   s^0, \goesto{})$, where $S = Q \times \valuations{V}$, $s^0 =
   (q^0, \val{0}{})$ and $\goesto{}$ is the minimal transition
-  relation satisfying the following rule:
+  relation satisfying the rule
   %
@@
       \and
-      v \models g
-      \and
-      v' = v[e]
+      \val{}{} \models g
+      \and
+      \val[\primeit]{}{} = \tilde{\val{}{}}[e]
+      \and
+      \valdiff{\val{}{}}{\tilde{\val{}{}}} \subseteq \export(a)
     }{
-      (q, v) \goesto{a} (q', v')
+      (q, \val{}{}) \goesto{a,\tilde{\val{}{}}} (q', \val[\primeit]{}{})
     }
@@
   \end{equation}
-  The \emph{closed semantics} of $B$ is given by the LTS
+  %
+  \todoSB{Do we actually need this?}
+  \hl{The \emph{closed semantics} of $B$ is given by the LTS
   $\semclosed{B} \bydef{=}\reachable{\semopen{B}}$, comprising
-  only the reachable states of $\semopen{B}$.
+  only the reachable states of $\semopen{B}$.}
 \end{definition}
+
+The use of the intermediate valuation $\tilde{\val{}{}}$ in the
+conclusion and the third premise of rule \eq{comp:semantics}
+allows some of the variables to get new values before the
+transition is actually fired.  Thus the component is \emph{open}
+to the exchange of data with its environment.  However, the
+fourth premise in \eq{comp:semantics} restricts the set of
+variables, which can be affected by such data transfer, to those
+that are exported through the ports participating in the
+interaction.
 
@@
   \label{defn:im}
-  Let $\cB = \{B_1,\dots,B_n\}$ be a finite set of
-  components with $B_i = (Q_i, q^0_i, P_i, V_i, \val{0}{i},
-  \goesto{})$,\footnote{%
-%
-    Here and below, we skip the index on the transition
-    relation $\goesto{}$, since it is always clear from the
-    context.
-%
-} such that all their respective components (\ie $Q_i$, $P_i$,
-  and $V_i$) are pairwise disjoint, \ie $\forall i \neq j,\ Q_i
-  \cap Q_j = P_i \cap P_j = V_i \cap V_j = \emptyset$.  Let $P =
-  \bigcup_{i = 1}^n P_i$ and $V = \bigcup_{i = 1}^n V_i$.
-
-  An \emph{interaction model over $(P,V)$} is a set $\Gamma
+  Consider a finite set of components $\cB = (Q_i, q^0_i, V_i,
+  \val{0}{i}, P_i, \export[i], \goesto{})^{i \in I}$, such that
+  all their respective components (\ie $Q_i$, $P_i$, and $V_i$)
+  are pairwise disjoint, \ie $\forall i \neq j,\ Q_i \cap Q_j =
+  P_i \cap P_j = V_i \cap V_j = \emptyset$.  Let $P = \bigcup_{i
+  \in I} P_i$ and $V = \bigcup_{i \in I} V_i$.
+%
+  For a set of ports $a \subseteq P$, we denote $\supp{a}
+  \bydef{=} \setdef{i \in I}{a \cap P_i \neq \emptyset}$ the
+  \emph{support} of $a$,
+  \noteSB{Updated this}\hl{and $V_a \bydef{=} \bigcup_{i \in
+    \supp{a}} \export[i](a \cap P_i)$ the set of component
+  variables exported for $a$.}
+
+  An \emph{interaction model over \hl{$(V,P)$}} is a set $\Gamma
   \subseteq 2^P \times \guards{V} \times \exprs{V}$, such that,
@@
   associated to the \emph{interaction} $a$ satisfy, respectively,
-  $g \in \guards{V_a}$ and $e \in \exprs{V_a}$, with $V_a
-  \bydef{=} \bigcup_{i:\, a \cap P_i \neq \emptyset} V_i$.  We
-  denote $\supp{a} \bydef{=} \setdef{i \in [1,n]}{a \cap P_i \neq
-    \emptyset}$ the \emph{support} of the interaction $a$.
-\noteLH{why not introduce supp earlier and use it for $V_a$?}
+  $g \in \guards{V_a}$ and $e \in \exprs{V_a}$.\footnote{%
+%
+    Notice that this definition allows $(\emptyset, \true,
+    \noop)$ and $(\emptyset, \false, \noop)$ to be included in
+    $\Gamma$.
+%
+  }
   %% We call the set of ports $P$ the \emph{domain} of the
@@
   The \emph{composition of $\cB$ with the interaction model
-    $\Gamma$} is the component $\Gamma(\cB) = (Q, q^0, P, V,
-  \val{0}, \goesto{})$, where $Q = \prod_{i=1}^n Q_i$, $q^0 =
-  q_1^0\dots q_n^0$, $\val{0}{}: V \rightarrow \data$ is such
-  that, for any $v \in V_i$, $\val[v]{0}{} = \val[v]{0}{i}$, and
-  $\goesto{}$ is the minimal transition relation satisfying
-  following rules:
-%
-  \begin{mathpar}
-    \infer{
-      q_i \goesto{\emptyset, \true, \noop} q_i'
-    }{
-      q_1 \dots q_i \dots q_n \goesto{\emptyset, \true, \noop} q_1 \dots q_i' \dots q_n
-    }\,,
-
+    $\Gamma$} is the component
+  $\Gamma(\cB) = (Q, q^0, V, \val{0}{}, P, \export, \goesto{})$,
+  where
+%
+  $Q = \prod_{i \in I} Q_i$;
+%
+  $q^0 = (q_i^0)^{i \in I}$;
+%
+  $\val{0}{}: V \rightarrow \data$ is such that, for any $v \in
+  V_i$, $\val{0}{}(v) = \val{0}{i}(v)$;
+%
+  $\export : P \rightarrow 2^V$ is such that, for any $p \in
+  P_i$, $\export(p) = \export[i](p)$;
+%
+  and $\goesto{}$ is the minimal transition relation satisfying
+  the rule
+%
+  \begin{gather}
+%%     \label{eq:im:empty}
+%%     \infer{
+%%       q_j \goesto{\emptyset, g, e} q_j'
+%%       \and
+%%       \forall i \neq j, q_i = q_i'
+%%     }{
+%%       (q_i)^{i \in I} \goesto{\emptyset, g, e} (q_i')^{i \in I}
+%%     }\,,
+%% %
+%%     \\[0.5\baselineskip]
+    \label{eq:im:int}
+%
     \infer{    
@@
       \and
+      a \neq \emptyset
+      \and
       \forall i \in \supp{a}, q_i \goesto{a \cap P_i, g_i, e_i} q_i'
@@
       \forall i \not\in \supp{a}, q_i = q_i'
+%
       \\\\
+      \textstyle
+%
       G = g \land \bigwedge_{i \in \supp{a}} g_i
       \and
-      E = e; (e_i)_{i \in \supp{a}}
+      E = e; (e_i)^{i \in \supp{a}}
     }{
-      q_1\dots q_n \goesto{a, G, E} q_1'\dots q_n'
+      (q_i)^{i \in I} \goesto{a, G, E} (q_i')^{i \in I}
     }\,.
-  \end{mathpar}
+  \end{gather}
 \end{definition}
@@
   \label{defn:arch}
-  An \emph{architecture} is a tuple $A = (\cC, P_A, V_A, \Gamma)$,
+  An \emph{architecture} is a tuple $A = (\cC, V_A, P_A, \Gamma)$,
   where $\cC$ is a finite set of \emph{coordinating components}
@@
   $\Gamma \subseteq 2^{P_A} \times \guards{V_A} \times \exprs{V_A}$
-  is an interaction model over $(P_A, V_A)$.
+  is an interaction model over \hl{$(V_A, P_A)$}.
 \end{definition}
@@
   \label{defn:arch:application}
-  Let $A = (\cC, P_A, V_A, \Gamma)$ be an architecture and let $\cB$
+  Let $A = (\cC, V_A, P_A, \Gamma)$ be an architecture and let $\cB$
   be a set of components, such that
@@
   \begin{align}
+    \bigcup_{B \in \cB} V_B \cap \bigcup_{C \in \cC} V_C = \emptyset\,,
+    &&
+    V_A \subseteq V \bydef{=} \bigcup_{B \in \cB \cup \cC} V_B\,,
+    \\
     \bigcup_{B \in \cB} P_B \cap \bigcup_{C \in \cC} P_C = \emptyset\,,
@@
     P_A \subseteq P \bydef{=} \bigcup_{B \in \cB \cup \cC} P_B\,,
-    \\
-    \bigcup_{B \in \cB} V_B \cap \bigcup_{C \in \cC} V_C = \emptyset\,,
-    &&
-    V_A \subseteq V \bydef{=} \bigcup_{B \in \cB \cup \cC} V_B\,,
   \end{align}
 %
-  and, denoting, for any $(a, g, e) \in \Gamma$, $V_a \bydef{=}
-  \bigcup_{B \in \supp{a}} V_B$, we have $g \in \guards{V_a}$ and
-  $e \in \exprs{V_a}$.
+  and
+  %% , denoting, for any $(a, g, e) \in \Gamma$, $V_a \bydef{=}
+  %% \bigcup_{B \in \supp{a}} \export[B](a \cap P_B)$, we have
+  $g \in \guards{V_a}$ and
+  $e \in \exprs{V_a}$ (see \defn{im} for the notation $V_a$).
 %
@@
 
+\todoSBin{Define equivalence $\arequiv$?}
+
 An architecture $A$ enforces coordination constraints on the
-components in $\cB$.  The interface $(P_A, V_A)$ of an
+components in $\cB$.  The interface \hl{$(V_A, P_A)$} of an
 architecture $A$ contains all ports of the coordinating
@@
   \label{defn:arch:composition}
-  Let $A_i = (\cC_i, P_{A_i}, V_{A_i}, \Gamma_i)$, for $i = 1,2$,
+  Let $A_i = (\cC_i, V_{A_i}, P_{A_i}, \Gamma_i)$, for $i = 1,2$,
   be two architectures.  The \emph{composition} of $A_1$ and
   $A_2$ is the architecture $A_1 \arcomp A_2 = (\cC_1 \cup \cC_2,
-  P_{A_1} \cup P_{A_2}, V_{A_1} \cup V_{A_2}, \Gamma)$, where
+  V_{A_1} \cup V_{A_2}, P_{A_1} \cup P_{A_2}, \Gamma)$, where
 %
@@
   \emptyset, \{\emptyset\}\bigr)$ is its neutral element, \ie for
-  any architecture $A$, we have $A \oplus A_{id} = A$.
+  any architecture $A$, we have $A \oplus A_{id} \arequiv A$.
   Furthermore, for any component $B$, we have $A_{id}(B) = B$.
-  %PCA: replaced ``holds'' by ``we have''
 \end{proposition}
@@
   A'(\cB)$.  Since this holds for any set of components $\cB$, we
-  conclude that $A \arcomp A' = A = A'$.
+  conclude that $A \arcomp A' \arequiv A \arequiv A'$.
 %
@@
 \label{secn:safety}
+
+For a component $B$, we denote $S_{\semopen{B}}$,
+$s^0_{\semopen{B}}$ the corresponding constituents of
+$\semopen{B}$.
+
+\begin{definition}[Safety properties]
+  \label{defn:property}
+  Let $B$ be a component.  A \emph{safety property} (below,
+  simply \emph{property}) of $B$ is a state predicate $\Phi:
+  S_{\semopen{B}} \rightarrow \sB$, such that $\bigl((q,
+  \val{}{}) \models \Phi\bigr) \land (\val[\primeit]{}{} \order
+  \val{}{})$ implies $(q, \val[\primeit]{}{}) \models \Phi$,
+  where we write $(q, \val{}{}) \models \Phi$ iff $\Phi(q,
+  \val{}{}) = \true$.  A property $\Phi$ is \emph{initial} if
+  $s^0_{\semopen{B}} \models \Phi$\todoSB{Do we need this?}\hl{;
+    it is \emph{reachable} iff there exists a possibly empty path
+    $s^0_{\semopen{B}} \goesto{a^1, \val{1}{}} s^1 \goesto{a^2,
+      \val{2}{}} \cdots \goesto{a^n, \val{n}{}} s^n$, such that
+    $s^n \models \Phi$}.
+\end{definition}
+
+\todoSB{Cite the original paper somewhere.}
+The main idea of our approach is that an architecture enforces
+its characteristic property on the set of its operand components.
+From this point of view, the set of coordinating components is
+not relevant, neither are their states.  Thus, to talk about
+properties enforced by architectures, we consider properties on
+the unrestricted composition of the operand components as
+formalized by the following definition.
+
+\begin{definition}[Enforcing properties]
+  \label{defn:impose}
+  Let $A = (\cC, P_A, V_A, \Gamma)$ be an architecture; let $\cB$
+  be a set of components and $\Phi$ an initial property of
+  their parallel composition $A_{id}(\cB)$ (see
+  \prop{arcomp:nice}).  We say that \emph{$A$ enforces $\Phi$ on
+    $\cB$} iff, for every state $s = (s_b, s_c)$ reachable in
+  $\semopen{A(\cB)}$, with $s_b \in \prod_{B\in \cB}
+  S_{\semopen{B}}$ and $s_c \in \prod_{C \in \cC}
+  S_{\semopen{C}}$, we have $s_b \models \Phi$.
+\end{definition}
+
+According to the above definition, when we say that an
+architecture enforces some property $\Phi$, it is implicitly
+assumed that $\Phi$ is initial for the coordinated components.
+Below, we omit mentioning this explicitly.
+
+\begin{theorem}[Preserving enforced properties]
+  \label{thm:combining}
+  Let $\cB$ be a set of components; let $A_i = (\cC_i, V_{A_i},
+  P_{A_i}, \Gamma_i)$, for $i = 1,2$, be two architectures
+  enforcing on $\cB$ the properties $\Phi_1$ and $\Phi_2$
+  respectively.  The composition $A_1 \arcomp A_2$ enforces on
+  $\cB$ the property $\Phi_1 \land \Phi_2$.
+\end{theorem}
+
+\begin{lemma}
+  \label{lem:onlyone}
+  Let $A = (\cC, V_A, P_A, \Gamma)$ be an architecture and denote
+  by $\Gamma_\cC \bydef{=}
+%
+  \setdef{
+    (a \cap P_\cC, \true, \noop)
+  }{
+    (a, g, e) \in \Gamma
+  }$, with $P_\cC = \bigcup_{C \in \cC} P_C$,
+%  
+  the projection of $\Gamma$ onto the coordinating components of
+  $A$.  Consider the architecture $A' = (\{C'\}, V_A, P_A,
+  \Gamma)$, where $C' = \Gamma_\cC(\cC)$.  For any set of
+  components $\cB$, satisfying the conditions of
+  \defn{arch:application}, we have
+  $\semopen{A(\cB)} = \semopen{A'(\cB)}$.
+\end{lemma}
+%
+\begin{proof}
+  First of all, notice that, by \defn{im},
+  $V_{C'} = \bigcup_{C \in \cC} V_C$ and $P_{C'} = P_\cC$.
+  The conditions of \defn{arch} are satisfied and $A'$ is indeed
+  an architecture.  Furthermore, $\cB$ satisfies the conditions
+  of \defn{arch:application} \wrt $A'$.  Hence, the component
+  $A'(\cB)$ is well defined.
+
+  Clearly the state spaces, initial states and interfaces of both
+  components coincide.  Thus we only have to prove that so do the
+  transition relations.  Let us assume that
+  $\cC = (C_i)^{i \in I}$ and $\cB = (B_j)^{j \in J}$.
+  We will use $q^i, q^{i\prime}$ to denote the states of
+  $C_i$ and $q_j, q_j'$ to denote the states of $B_j$,
+  and similarly for the valuations of variables.
+
+  By \defn{comp:semantics}, a transition
+%
+  \begin{equation}
+    \label{eq:lem1:trans:sem}
+    (q^i, \val{i}{})^{i \in I} (q_j, \val{}{j})^{j \in J}
+    \goesto{a, \val[\tilde]{}{}}
+    (q^{i\prime}, \val{i\prime}{})^{i \in I}
+    (q_j', \val{\prime}{j})^{j \in J}
+  \end{equation}
+%  
+  is a transition in $\semopen{A(\cB)}$ (\resp
+  $\semopen{A'(\cB)}$) iff
+%
+  \begin{equation}
+    \label{eq:lem1:trans}
+    (q^i)^{i \in I} (q_j)^{j \in J}
+    \goesto{a, G, E}
+    (q^{i\prime})^{i \in I} (q_j')^{j \in J}
+    \,,
+  \end{equation}
+%
+  is a transition in $A(\cB)$ (\resp $A'(\cB)$) and
+%
+  \begin{mathpar}
+    (\val{i}{})^{i \in I} (\val{}{j})^{j \in J}
+    \models G
+    \,,
+    \and
+    (\val{i\prime}{})^{i \in I} (\val{\prime}{j})^{j \in J}
+    = \val[\tilde]{}{}[E]
+    \,,
+    \and
+    \valdiff{(\val{i}{})^{i \in I} (\val{}{j})^{j \in J}}{
+      \val[\tilde]{}{}} \subseteq \export(a)
+    \,.   
+  \end{mathpar}
+
+  By \defn{im}, \eq{lem1:trans} is a transition in $A(\cB)$
+  iff $a \neq \emptyset$, $(a, g, e) \in \IMextend{\Gamma}{P}$,
+  where $P = \bigcup_{B \in \cB \cup \cC} P_B$, and
+  %
+  \begin{enumerate}
+  \item for $i \in I$,
+    $q^i \goesto{a \cap P_{C_i}, g_{C_i}, e_{C_i}} q^{i\prime}$
+    is a transition in $C_i$, or
+    $a \cap P_{C_i} = \emptyset$ and $q^i = q^{i\prime}$,
+    $g_{C_i} = \true$ and $e_{C_i} = \noop$\,;
+  \item for $j \in J$,
+    $q_j \goesto{a \cap P_{B_j}, g_{B_j}, e_{B_j}} q_j'$
+    is a transition in $B_j$, or
+    $a \cap P_{B_j} = \emptyset$ and $q_j = q_j'$,
+    $g_{B_j} = \true$ and $e_{B_j} = \noop$\,;
+  \item $G = g \land \bigwedge_{i \in I} g_{C_i} \land
+    \bigwedge_{j \in J} g_{B_j}$ and
+    $E = e; (e_{C_i})^{i \in I} (e_{B_j})^{j \in J}$.
+  \end{enumerate}
+  %
+
+  Similarly, \eq{lem1:trans} is a transition in
+  $A'(\cB)$ iff $a \neq \emptyset$,
+  $(a, g, e) \in \IMextend{\Gamma}{P}$ and
+  %
+  \begin{enumerate}
+  \item \label{only1:coord}
+    $(q^i)^{i \in I}
+    \goesto{a \cap P_{C'}, g_{C'}, e_{C'}}
+    (q^{i\prime})^{i \in I}$ is a transition in $C'$,
+    or $a \cap P_{C'} = \emptyset$ and $q^i = q^{i\prime}$,
+    for all $i \in [1,m]$,
+    $g_{C'} = \true$ and $e_{C'} = \noop$\,;
+  \item for $j \in J$,
+    $q_j \goesto{a \cap P_{B_j}, g_{B_j}, e_{B_j}} q_j'$
+    is a transition in $B_j$, or
+    $a \cap P_{B_j} = \emptyset$ and $q_j = q_j'$,
+    $g_{B_j} = \true$, and $e_{B_j} = \noop$;
+  \item $G = g \land g_{C'} \land
+    \bigwedge_{j \in J} g_{B_j}$ and
+    $E = e; e_{C'}, (e_{B_j})^{j \in J}$.
+%
+  \breakenumistart
+  Notice that, for any $i \in I$, since
+  $P_{C_i} \subseteq P_{C'}$, we have
+  $a \cap P_{C_i} = (a \cap P_{C'}) \cap P_{C_i}$.
+  Thus, if $a \cap P_{C'} \neq \emptyset$, 
+  the transition in condition~\ref{only1:coord} above is
+  present in $C'$ iff
+  $(a \cap P_{C'}, \true, \noop) \in \Gamma_\cC$ and
+  \breakenumiend
+% 
+  \item for $i \in I$,
+    $q^i \goesto{a \cap P_{C_i}, g_{C_i}, e_{C_i}} q^{i\prime}$
+    is a transition in $C_i$, or $a \cap P_{C_i} = \emptyset$
+    and $q^i = q^{i\prime}$,
+    $g_{C_i} = \true$ and $e_{C_i} = \noop$,
+  \item $g_{C'} = \bigwedge_{i \in I} g_{C_i}$ and
+    $e_{C'} = (e_{C_i})^{i \in I}$.
+  \end{enumerate}
+
+  Consider $(a,g,e) \in \IMextend{\Gamma}{P}$.  By
+  \eq{im:extension}, this is equivalent to
+  $(a \cap P_A, g, e) \in \Gamma$.
+  Since $P_{C'} = P_\cC \subseteq P_A$, we have
+  $a \cap P_{C'} = a \cap P_\cC = (a \cap P_A) \cap P_\cC$.
+  Hence, this is also equivalent to
+  $(a \cap P_{C'}, \true, \noop) \in \Gamma_\cC$,
+  which concludes the proof.
+\end{proof}
+
+\begin{lemma}
+  \label{lem:onestep}
+  Let $\cB$ be a set of components; let $A_i = (\{C_i\}, V_{A_i},
+  P_{A_i}, \Gamma_i)$, for $i = 1,2$, be two architectures
+  applicable to $\cB$, with one coordinator each, and denote
+  $P_i = P_{C_i} \cup \bigcup_{B \in \cB} P_B$.
+  Finally, let
+%
+  $
+  s_1 s_2 s
+%
+  \goesto{a, \tilde{\val{}{}}}
+%
+  s_1' s_2' s'
+  $,
+%
+  be a transition in $\semopen{(A_1 \arcomp A_2)(\cB)}$, with
+  $a \neq \emptyset$, 
+  $s, s' \in \prod_{B \in \cB} S_{\semopen{B}}$
+  and
+  $s_i, s_i' \in S_{\semopen{C_i}}$ ($i=1,2$).
+%
+  Then, for $i=1,2$, either $a \cap P_i = \emptyset$ and $s_i s=
+  s_i' s'$, or there exists a transition
+%
+  $
+  s_i s
+%
+  \goesto{a \cap P_i, \val[\doubletilde]{}{}}
+%
+  s_i' s''
+  $ 
+%
+  in $\semopen{A_i(\cB)}$, with
+  $\val[\doubletilde]{}{}$ being the restriction of
+  $\val[\tilde]{}{}$ to
+  $V_1 = V_{C_1} \cup \bigcup_{B \in \cB} V_B$ and
+  $s' \order s''$.
+\end{lemma}
+%
+\begin{proof}
+  By \defn{comp:semantics}, every semantic state consists of a
+  component state and a valuation of component variables.  Thus,
+  we have
+%
+  \[
+  (q_1, \val{}{1}, q_2, \val{}{2}, q, \val{}{})
+%
+  \goesto{a, \tilde{\val{}{}}}
+%
+  (q_1', \val[\primeit]{}{1}, q_2', \val[\primeit]{}{1}, q', \val[\primeit]{}{})
+  \,.
+  \]
+%
+  By \eq{comp:semantics} and \eq{im:int}, this implies
+  $(q_1, q_2, q) \goesto {a, G, E} (q_1', q_2', q')$, with
+%
+  $G = g \land g_1 \land g_2 \land g_b$
+  and
+  $E = e; (e_1, e_2, e_b)$,
+  where
+%    
+  \begin{mathpar}
+    g_b = \bigwedge_{B \in \supp{a} \cap \cB} g_B
+    \,,
+    \and
+    e_b = (e_B)^{B \in \supp{a} \cap \cB}
+  \end{mathpar}
+%
+  and such that $(a, g, e) \in \Gamma$ (see
+  \eq{arch:composition}) and
+%
+  \begin{align}
+    \label{eq:guard}
+    (\val{}{1}, \val{}{2}, \val{}{}) &\models G
+    \,,
+    \\
+    \label{eq:substitution}
+    (\val[\primeit]{}{1}, \val[\primeit]{}{2}, \val[\primeit]{}{})
+    &= \val[\tilde]{}{}[E]
+    \,,
+    \\
+    \label{eq:transient}
+    \valdiff{(\val{}{1}, \val{}{2}, \val{}{})}{\val[\tilde]{}{}}
+    &\subseteq \export(a)
+    \,.
+  \end{align}
+%
+  If $a \cap P_1 = \emptyset$, then $\supp{a} = \{C_2\}$ and, by
+  \eq{transient} and \defn{im}, $s_1 = s_1'$ and $s = s'$
+  (recall, \defn{im}, that, for $(a,g,e) \in \Gamma$, we have $e
+  \in \exprs{V_a}$).  Hereafter, assume $a \cap P_1 \neq
+  \emptyset$.
+
+  Denoting $P_b = \bigcup_{B \in \supp{a} \cap \cB} P_B$, we
+  have, by \eq{im:int},
+%
+  \begin{mathpar}
+    q_1 \goesto{a \cap P_{C_1}, g_1, e_1} q_1'
+    \and
+    \text{and}
+    \and
+    q \goesto{a \cap P_b, g_b, e_b} q'
+    \,.
+  \end{mathpar}
+
+  By \eq{arch:composition}, for $i=1,2$, there exist
+  $(a \cap P_{A_i}, g^i, e^i) \in \Gamma_i$,
+  such that $g = g^1 \land g^2$ and $e = e^1 \land e^2$.
+  By \eq{guard}, we have
+  $(\val{}{1}, \val{}{}) \models g^1 \land g_1 \land g_b$.
+
+  Denoting $\val[\doubletilde]{}{}$ the restriction of
+%
+  $\val[\tilde]{}{}$ to
+  $V_1 = V_{C_1} \cup \bigcup_{B \in \cB} V_B$,
+%
+  we have, by \eq{substitution} and the monotonicity of
+  expressions,
+%
+  $(\val[\primeit]{}{1}, \val[\primeit]{}{}) \order
+  \val[\doubletilde]{}{}[e^1; (e_1, e_b)]$.  Notice that all
+  variables affected by both $e^1$ and $e^2$ must necessarily
+  belong to $\bigcup_{B \in \cB} V_B$.  Hence,
+%
+  $\val[\doubletilde]{}{}[e^1; (e_1, e_b)] =
+  (\val[\primeit]{}{1}, \val[\doubleprimeit]{}{})$ with 
+  $\val[\primeit]{}{} \order \val[\doubleprimeit]{}{}$.
+
+  By \eq{comp:semantics} and \eq{im:int}, we have
+  \[
+  (q_1, \val{}{1}, q, \val{}{})
+  \goesto{a \cap P_1, \val[\doubletilde]{}{}}
+  (q_1', \val[\primeit]{}{1}, q, \val[\doubleprimeit]{}{})
+  \,.
+  \]
+\end{proof}
+
+\begin{lemma}
+  \label{lem:stepabove}
+  Consider a component $B$ and let 
+%
+  $
+  (q_1, \val{}{1})
+%
+  \goesto{a, \val[\tilde]{}{}}
+%
+  (q_2, \val{}{2})
+  $,
+%
+  be a transition in $\semopen{B}$.  For any valuation
+  $\val[\primeit]{}{1}$, such that
+  $\val{}{1} \order \val[\primeit]{}{1}$ and
+  $\valdiff{\val{}{1}}{\val[\primeit]{}{1}} \subseteq \export(a)$,
+  there exists a transition
+%
+  $
+  (q_1, \val[\primeit]{}{1})
+%
+  \goesto{a, \val[\tilde]{}{}}
+%
+  (q_2, \val{}{2})
+  $
+%
+  in $\semopen{B}$.
+\end{lemma}
+%
+\begin{proof}
+  By \eq{comp:semantics}, we have
+%
+  \begin{mathpar}
+    q_1 \goesto{a, g, e} q_2
+    \,,
+    \and
+    \val{}{1} \models g
+    \,,
+    \and
+    \val{}{2} = \val[\tilde]{}{}[e]
+    \,,
+    \and
+    \text{and}
+    \and
+    \valdiff{\val{}{1}}{\val[\tilde]{}{}} \subseteq \export(a)
+    \,.
+  \end{mathpar}
+
+  By monotonicity of guards, we deduce
+  $\val[\primeit]{}{1} \models g$.
+  For any $v \in \export(a)$,
+  $\val[\primeit]{}{1}(v) = \val{}{1}(v) = \val[\tilde]{}{}(v)$.
+  Hence, 
+  $\valdiff{\val[\primeit]{}{1}}{\val[\tilde]{}{}}
+  \subseteq \export(a)$.
+  By \eq{comp:semantics}, we conclude 
+%
+  $
+  (q_1, \val[\primeit]{}{1})
+%
+  \goesto{a, \val[\tilde]{}{}}
+%
+  (q_2, \val{}{2})
+  $.  
+\end{proof}
+
+\begin{proof}[Proof of \thm{combining}]
+  By \lem{onlyone}, we can assume that each of the two
+  architectures has only one coordinating component.  For $i =
+  1,2$, we denote $\{C_i\} = \cC_i$, $P_i = P_{C_i}
+  \cup\ \bigcup_{B \in \cB} P_B$ and $V_i = V_{C_i}
+  \cup\ \bigcup_{B \in \cB} V_B$.
+
+  The initiality of $\Phi_1 \land \Phi_2$, is trivial: both
+  $\Phi_1$ and $\Phi_2$ are initial, hence $s^0 \models \Phi_1
+  \land \Phi_2$.
+
+  Consider a path
+%
+  \[
+  s^0_1 s^0_2 s^0
+%
+  \goesto{a^1, \val[\tilde]{1}{}}
+%
+  s^1_1 s^1_2 s^1
+%
+  \goesto{a^2, \val[\tilde]{2}{}}
+  \cdots
+  \goesto{a^k, \val[\tilde]{k}{}}
+%
+  s^k_1 s^k_2 s^k
+  \]
+%
+  in $\semopen{(A_1 \arcomp A_2)(\cB)}$, where
+  $s^0,\dots,s^k \in \prod_{B \in \cB} S_{\semopen{B}}$ and
+  $s^0_i,\dots, s^k_i \in S_{\semopen{C_i}}$, for $i=1,2$.
+  We have to show that $s^k \models \Phi_1 \land \Phi_2$.
+
+  Assuming that $a^1 \cap P_1 \neq \emptyset$, by \lem{onestep},
+  there exists $s^{1\prime} \in \prod_{B \in \cB} S_{\semopen{B}}$,
+  such that
+%
+  \[
+  s^0_1 s^0
+%
+  \goesto{a^1 \cap P_1, \val[\doubletilde]{1}{}}
+%
+  s^1_1 s^{1\prime}
+  \]
+%
+  is a transition in $\semopen{A_1(\cB)}$ with
+  $\val[\doubletilde]{1}{}$ being the restriction of
+  $\val[\tilde]{1}{}$ to $V_1$ and
+  $s^1 \order s^{1\prime}$.
+%
+  By \lem{stepabove}, 
+  \[
+  s^1_1 s^1_2 s^{1\prime}
+%
+  \goesto{a^2, \val[\tilde]{2}{}}
+%
+  s^2_1 s^2_2 s^2
+  \]
+  is a transition in $\semopen{(A_1 \arcomp A_2)(\cB)}$ and,
+  therefore, 
+  \[
+  s^1_1 s^1_2 s^{1\prime}
+%
+  \goesto{a^2, \val[\tilde]{2}{}}
+%
+  s^2_1 s^2_2 s^2
+%
+  \goesto{a^3, \val[\tilde]{3}{}}
+  \cdots
+  \goesto{a^k, \val[\tilde]{k}{}}
+%
+  s^k_1 s^k_2 s^k
+  \]
+%  
+  is a path in $\semopen{(A_1 \arcomp A_2)(\cB)}$.
+%
+  Notice that, if the above assumption, $a^1 \cap P_1 \neq
+  \emptyset$, does not hold, then $s^0_1 = s^1_1$, $s^0 = s^1$
+  and we can take $s^{1\prime} = s^1$ in this latter path.
+
+  Repeating the entire argument $k-1$ times, starting with this
+  shorter path, we obtain a path
+%
+  \begin{equation}
+    \label{eq:path-in-1}
+    s^0_1 s^0
+    %
+    \goesto{a^1 \cap P_1, \val[\doubletilde]{1}{}}
+    %
+    s^1_1 s^{1\prime}
+    %
+    \goesto{a^2 \cap P_1, \val[\doubletilde]{2}{}}
+    %
+    s^2_1 s^{2\prime}
+    %
+    \goesto{a^3 \cap P_1, \val[\doubletilde]{3}{}}
+    \cdots
+    \goesto{a^k \cap P_1, \val[\doubletilde]{k}{}}
+    %
+    s^k_1 s^{k'}
+  \end{equation}
+%  
+  with $s^i \order s^{i\prime}$, for all $i \in [1,k]$.
+
+  From \eq{path-in-1}, we conclude that the state $s^k_1
+  s^{k\prime}$ is reachable in $\semopen{A_1(\cB)}$.  Since $A_1$
+  enforces $\Phi_1$ on $\cB$, this implies that $s^{k\prime}
+  \models \Phi_1$.  Since $s^k \order s^{k\prime}$, we deduce, by
+  \defn{property}, that $s^k \models \Phi_1$.
+
+  Symmetrically, $s^k \models \Phi_2$, which concludes
+  the proof.
+\end{proof}
 
@@
 $t\in\AlgT$, and $iv(t)$ returns its input variables.
-Action algebras can encode naturally usual point-to-point message passing calculi (using 
-$a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs), but it also allows
+
+pNets can encode naturally the notion of input actions in value-passing CCS
+\cite{Milner89} or of usual point-to-point message passing calculi, but it also allows
 for more general mechanisms, like gate negociation in Lotos, or broadcast
-communications.
+communications. Using our notations, value-passing actions \emph{\`a la} CCS would be
+encoded as $a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs (in which $v_i$ are 
+action terms containing no input variables). 
+%For Lotos-style
+%distributed synchronisation, we use synchronisation vectors that encode matching data
+%offers on a common gate; or 
+We can also use more complex action structure such as Meije-SCCS action
+monoids, like in $a.b$, $a^{f(n)}$ (see \cite{deSimone85}). The expressiveness of the 
+synchronisation constructs
+will depend on the action algebra.
 
@@
 $s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
-		J}\rangle} s'\in \to $ then 
-% REMOVED BECAUSE USELESS: $\iv(\alpha)\!\subseteq\! \vars(s')$, 
+		J}\rangle} s'\in \to $ then $\iv(\alpha)\!\subseteq\! \vars(s')$, 
 		$\vars(\alpha)\backslash \iv(\alpha)\!\subseteq\! \vars(s)$, 
-		$\vars(e_b)\!\subseteq\! \vars(s)\cup\varsigma(\alpha)$, and
-		$\forall j\!\in\! J .\,\vars(e_j)\!\subseteq\! \vars(s)\cup\varsigma(\alpha)\land 
+		$\vars(e_b)\!\subseteq\! \vars(s')$, and
+		$\forall j\!\in\! J .\,\vars(e_j)\!\subseteq\! \vars(s)\land 
 		x_j\!\in\!\vars(s')$. %,  and $s= s'\Rightarrow J=\emptyset$.
@@
 A composite pNet consists of a set of sub-pNets exposing
-a set of actions, each of them synchronising actions in each of
+a set of actions, each of them triggering internal actions in each of
 the sub-pNets. The synchronisation between global actions and
@@
 Actions involved at the pNet level (in the synchronisation vectors) do
-not need to distinguish  input 
+not need to distinguish between input and output
 variables. Action terms for pNets are defined as follows:
@@
   synchronisation vectors ($K\in\I_\P$). $\forall k\!\in\! K,
-  \symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k\,|\,g_k$ where
+  \symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k$ where
   $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
@@
   J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
-$\Label(\symb{SV}_k) = \alpha'_k$. $g_k \in \AlgB$ is a guard associated to the vector 
-$\vars(g_k)\subseteq \bigcup_{l\in I_k\uplus J_k}{\vars({\alpha_l})}$.
+$\Label(\symb{SV}_k) = \alpha'_k$.
 

### 2018-02-11 2018-Arch-pNets/arch-pNets.tex

@@
 
+\paragraph{Unifying notations -- remarks}
+
+\todoLHin{proposed notations:}
+$g$ are boolean expressions
+$e_i$ are updates/assignments
+
+\todoLHin{Remove term algebra or simplify?}
+\todoLHin{universal domain $\implies$ remove sort}
+\todoLHin{replace assignments by $e_i$}
+
+In Archi we have a whereas in pnets we have $\alpha$ where, approximately $\alpha = 
+a(x_1..x_n)$ except that a is port name in archi and action name in pnets.
+Is this true? can we unify better? or is it sufficient?
+
+states looks ok, but initial state is $s_0$ in pnet and not in archi : $s^0$ . exponent 
+position was removed from pnet because we found it complex with indexed set notation but 
+could be ok.
+
 \begin{definition}[Components]
@@
 $L$ is the set of labels of the form
-$\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in J}\rangle$,
-where $\alpha \in\AlgA$ is a parameterised action, $e_b \in
-\AlgB$ is a guard, and the variables $x_j\in P$
-are assigned the expressions $e_j\in \AlgE$.
+
+$\langle \alpha,~g,~e\rangle$,
+where $\alpha \in\AlgA$ is a parameterised action, $g$ is a guard, and the variables 
+$x_j\in \vars(s')$
+are assigned the updates in $e$.
 If 
-$s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
-		J}\rangle} s'\in \to $ then $\iv(\alpha)\!\subseteq\! \vars(s')$, 
+$s \xrightarrow{\langle \alpha,~g,~e\rangle} s'\in \to $ then 
+% REMOVED BECAUSE USELESS: $\iv(\alpha)\!\subseteq\! \vars(s')$, 
 		$\vars(\alpha)\backslash \iv(\alpha)\!\subseteq\! \vars(s)$, 
-		$\vars(e_b)\!\subseteq\! \vars(s')$, and
-		$\forall j\!\in\! J .\,\vars(e_j)\!\subseteq\! \vars(s)\land 
-		x_j\!\in\!\vars(s')$. %,  and $s= s'\Rightarrow J=\emptyset$.
+		$\vars(g)\!\subseteq\! \vars(s)\cup\vars(\alpha)$, and
+		$\vars(\codom(e))\!\subseteq\! \vars(s)\cup\vars(\alpha)\land 
+		\vars(\dom(e))\!\in\!\vars(s')$. %,  and $s= s'\Rightarrow J=\emptyset$.
 
@@
   J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
-$\Label(\symb{SV}_k) = \alpha'_k$.
+$\Label(\symb{SV}_k) = \alpha'_k$. $g_k $ is a guard associated to the vector 
+$\vars(g_k)\subseteq \bigcup_{l\in I_k\uplus J_k}{\vars({\alpha_l})}$.
 

### 2018-02-11 2018-Arch-pNets/arch-pNets.tex
A little bit of uniformisation + comments to Ludo's notes

@@
 \newcommand{\Ludo}{\\\hfill\mdash Ludo}
-\newcommand{\noteLH}[2][color=green!40, size=\tiny]{\todo[#1]{{#2}\Ludo}}
-\newcommand{\noteLHin}[2][inline,color=green!40]{\todo[#1]{{#2}\Ludo}}
-\newcommand{\todoLH}[2][color=green!40, size=\tiny]{\todo[#1]{\textbf{To-do Ludo:} {#2}}}
-\newcommand{\todoLHin}[2][inline,color=green!40]{\todo[#1]{\textbf{To-do Ludo: } {#2}}}
+\newcommand{\noteLH}[2][color=blue!40, size=\tiny]{\todo[#1]{{#2}\Ludo}}
+\newcommand{\noteLHin}[2][inline,color=blue!40]{\todo[#1]{{#2}\Ludo}}
+\newcommand{\todoLH}[2][color=blue!40, size=\tiny]{\todo[#1]{\textbf{To-do Ludo:} {#2}}}
+\newcommand{\todoLHin}[2][inline,color=blue!40]{\todo[#1]{\textbf{To-do Ludo: } {#2}}}
+
+\newcommand{\noteIn}[2][inline,color=black!20]{\todo[#1]{{#2}}}
 
@@
 
-%****************************************************************
-%****************************************************************
-
-\section{The theory of architectures with data}
-\label{secn:archs}
-
-%****************************************************************
-
-\subsection{Components and composition}
-\label{sec:components}
-
 \todoSBin{Preliminaries on the universal(?) data domain $\data$
@@
 
-\paragraph{Unifying notations -- remarks}
+\subsection*{Unifying notations -- remarks}
 
@@
 
-In Archi we have a whereas in pnets we have $\alpha$ where, approximately $\alpha = 
-a(x_1..x_n)$ except that a is port name in archi and action name in pnets.
+\noteIn{In Archi we have $a$, whereas in pNets we have $\alpha$, where, approximately $\alpha = 
+a(x_1..x_n)$, except that $a$ is port name in archi and action name in pNets.
 Is this true? can we unify better? or is it sufficient?
-
-states looks ok, but initial state is $s_0$ in pnet and not in archi : $s^0$ . exponent 
-position was removed from pnet because we found it complex with indexed set notation but 
+\Ludo
+
+$a$ is a set of ports, but otherwise, yes, this is true.  I think
+this is coherent, since, in archi, we have the ``interaction
+part'', \ie only ports, plus the data part, \ie variables,
+guards, expressions.  In pNets, these are combined.  So, it seems
+ok that notations differ\mdash ``uniformisation'' will be
+achieved by encoding archi $\rightarrow$ pNets.  \Simon }
+
+\noteIn{states looks ok, but initial state is $s_0$ in pNet and not in archi : $s^0$.  Exponent 
+position was removed from pNet because we found it complex with indexed set notation but 
 could be ok.
+\Ludo
+
+I am using exponent notation for ``modifiers'', reserving\mdash
+as much as possible\mdash index notation for enumeration.  I
+think this can be solved, where necessary, by using parentheses,
+\eg $(s^0_i)^{i \in I}$
+\Simon
+}
+
+%****************************************************************
+%****************************************************************
+
+\section{The theory of architectures with data}
+\label{secn:archs}
+
+%****************************************************************
+
+\subsection{Components and composition}
+\label{sec:components}
 
@@
       \and
-      E = e; (e_i)^{i \in \supp{a}}
+      E = e; e_i^{i \in \supp{a}}
     }{
@@
   \val{}{}) = \true$.  A property $\Phi$ is \emph{initial} if
-  $s^0_{\semopen{B}} \models \Phi$\todoSB{Do we need this?}\hl{;
-    it is \emph{reachable} iff there exists a possibly empty path
-    $s^0_{\semopen{B}} \goesto{a^1, \val{1}{}} s^1 \goesto{a^2,
-      \val{2}{}} \cdots \goesto{a^n, \val{n}{}} s^n$, such that
-    $s^n \models \Phi$}.
+  $s^0_{\semopen{B}} \models \Phi$.
+  %% \todoSB{Do we need this?}\hl{;
+  %% it is \emph{reachable} iff there exists a possibly empty path
+  %% $s^0_{\semopen{B}} \goesto{a^1, \val{1}{}} s^1 \goesto{a^2,
+  %%   \val{2}{}} \cdots \goesto{a^n, \val{n}{}} s^n$, such that
+  %% $s^n \models \Phi$}.
 \end{definition}
@@
   \prop{arcomp:nice}).  We say that \emph{$A$ enforces $\Phi$ on
-    $\cB$} iff, for every state $s = (s_b, s_c)$ reachable in
-  $\semopen{A(\cB)}$, with $s_b \in \prod_{B\in \cB}
-  S_{\semopen{B}}$ and $s_c \in \prod_{C \in \cC}
-  S_{\semopen{C}}$, we have $s_b \models \Phi$.
+    $\cB$} iff, for every state $s = (s_c, s_b)$ reachable in
+  $\semopen{A(\cB)}$, with 
+  $s_c \in \prod_{C \in \cC} S_{\semopen{C}}$ and
+  $s_b \in \prod_{B \in \cB} S_{\semopen{B}}$,
+  we have $s_b \models \Phi$.
 \end{definition}
@@
 \end{theorem}
-
-\begin{lemma}
-  \label{lem:onlyone}
-  Let $A = (\cC, V_A, P_A, \Gamma)$ be an architecture and denote
-  by $\Gamma_\cC \bydef{=}
-%
-  \setdef{
-    (a \cap P_\cC, \true, \noop)
-  }{
-    (a, g, e) \in \Gamma
-  }$, with $P_\cC = \bigcup_{C \in \cC} P_C$,
-%  
-  the projection of $\Gamma$ onto the coordinating components of
-  $A$.  Consider the architecture $A' = (\{C'\}, V_A, P_A,
-  \Gamma)$, where $C' = \Gamma_\cC(\cC)$.  For any set of
-  components $\cB$, satisfying the conditions of
-  \defn{arch:application}, we have
-  $\semopen{A(\cB)} = \semopen{A'(\cB)}$.
-\end{lemma}
-%
-\begin{proof}
-  First of all, notice that, by \defn{im},
-  $V_{C'} = \bigcup_{C \in \cC} V_C$ and $P_{C'} = P_\cC$.
-  The conditions of \defn{arch} are satisfied and $A'$ is indeed
-  an architecture.  Furthermore, $\cB$ satisfies the conditions
-  of \defn{arch:application} \wrt $A'$.  Hence, the component
-  $A'(\cB)$ is well defined.
-
-  Clearly the state spaces, initial states and interfaces of both
-  components coincide.  Thus we only have to prove that so do the
-  transition relations.  Let us assume that
-  $\cC = (C_i)^{i \in I}$ and $\cB = (B_j)^{j \in J}$.
-  We will use $q^i, q^{i\prime}$ to denote the states of
-  $C_i$ and $q_j, q_j'$ to denote the states of $B_j$,
-  and similarly for the valuations of variables.
-
-  By \defn{comp:semantics}, a transition
-%
-  \begin{equation}
-    \label{eq:lem1:trans:sem}
-    (q^i, \val{i}{})^{i \in I} (q_j, \val{}{j})^{j \in J}
-    \goesto{a, \val[\tilde]{}{}}
-    (q^{i\prime}, \val{i\prime}{})^{i \in I}
-    (q_j', \val{\prime}{j})^{j \in J}
-  \end{equation}
-%  
-  is a transition in $\semopen{A(\cB)}$ (\resp
-  $\semopen{A'(\cB)}$) iff
-%
-  \begin{equation}
-    \label{eq:lem1:trans}
-    (q^i)^{i \in I} (q_j)^{j \in J}
-    \goesto{a, G, E}
-    (q^{i\prime})^{i \in I} (q_j')^{j \in J}
-    \,,
-  \end{equation}
-%
-  is a transition in $A(\cB)$ (\resp $A'(\cB)$) and
-%
-  \begin{mathpar}
-    (\val{i}{})^{i \in I} (\val{}{j})^{j \in J}
-    \models G
-    \,,
-    \and
-    (\val{i\prime}{})^{i \in I} (\val{\prime}{j})^{j \in J}
-    = \val[\tilde]{}{}[E]
-    \,,
-    \and
-    \valdiff{(\val{i}{})^{i \in I} (\val{}{j})^{j \in J}}{
-      \val[\tilde]{}{}} \subseteq \export(a)
-    \,.   
-  \end{mathpar}
-
-  By \defn{im}, \eq{lem1:trans} is a transition in $A(\cB)$
-  iff $a \neq \emptyset$, $(a, g, e) \in \IMextend{\Gamma}{P}$,
-  where $P = \bigcup_{B \in \cB \cup \cC} P_B$, and
-  %
-  \begin{enumerate}
-  \item for $i \in I$,
-    $q^i \goesto{a \cap P_{C_i}, g_{C_i}, e_{C_i}} q^{i\prime}$
-    is a transition in $C_i$, or
-    $a \cap P_{C_i} = \emptyset$ and $q^i = q^{i\prime}$,
-    $g_{C_i} = \true$ and $e_{C_i} = \noop$\,;
-  \item for $j \in J$,
-    $q_j \goesto{a \cap P_{B_j}, g_{B_j}, e_{B_j}} q_j'$
-    is a transition in $B_j$, or
-    $a \cap P_{B_j} = \emptyset$ and $q_j = q_j'$,
-    $g_{B_j} = \true$ and $e_{B_j} = \noop$\,;
-  \item $G = g \land \bigwedge_{i \in I} g_{C_i} \land
-    \bigwedge_{j \in J} g_{B_j}$ and
-    $E = e; (e_{C_i})^{i \in I} (e_{B_j})^{j \in J}$.
-  \end{enumerate}
-  %
-
-  Similarly, \eq{lem1:trans} is a transition in
-  $A'(\cB)$ iff $a \neq \emptyset$,
-  $(a, g, e) \in \IMextend{\Gamma}{P}$ and
-  %
-  \begin{enumerate}
-  \item \label{only1:coord}
-    $(q^i)^{i \in I}
-    \goesto{a \cap P_{C'}, g_{C'}, e_{C'}}
-    (q^{i\prime})^{i \in I}$ is a transition in $C'$,
-    or $a \cap P_{C'} = \emptyset$ and $q^i = q^{i\prime}$,
-    for all $i \in [1,m]$,
-    $g_{C'} = \true$ and $e_{C'} = \noop$\,;
-  \item for $j \in J$,
-    $q_j \goesto{a \cap P_{B_j}, g_{B_j}, e_{B_j}} q_j'$
-    is a transition in $B_j$, or
-    $a \cap P_{B_j} = \emptyset$ and $q_j = q_j'$,
-    $g_{B_j} = \true$, and $e_{B_j} = \noop$;
-  \item $G = g \land g_{C'} \land
-    \bigwedge_{j \in J} g_{B_j}$ and
-    $E = e; e_{C'}, (e_{B_j})^{j \in J}$.
-%
-  \breakenumistart
-  Notice that, for any $i \in I$, since
-  $P_{C_i} \subseteq P_{C'}$, we have
-  $a \cap P_{C_i} = (a \cap P_{C'}) \cap P_{C_i}$.
-  Thus, if $a \cap P_{C'} \neq \emptyset$, 
-  the transition in condition~\ref{only1:coord} above is
-  present in $C'$ iff
-  $(a \cap P_{C'}, \true, \noop) \in \Gamma_\cC$ and
-  \breakenumiend
-% 
-  \item for $i \in I$,
-    $q^i \goesto{a \cap P_{C_i}, g_{C_i}, e_{C_i}} q^{i\prime}$
-    is a transition in $C_i$, or $a \cap P_{C_i} = \emptyset$
-    and $q^i = q^{i\prime}$,
-    $g_{C_i} = \true$ and $e_{C_i} = \noop$,
-  \item $g_{C'} = \bigwedge_{i \in I} g_{C_i}$ and
-    $e_{C'} = (e_{C_i})^{i \in I}$.
-  \end{enumerate}
-
-  Consider $(a,g,e) \in \IMextend{\Gamma}{P}$.  By
-  \eq{im:extension}, this is equivalent to
-  $(a \cap P_A, g, e) \in \Gamma$.
-  Since $P_{C'} = P_\cC \subseteq P_A$, we have
-  $a \cap P_{C'} = a \cap P_\cC = (a \cap P_A) \cap P_\cC$.
-  Hence, this is also equivalent to
-  $(a \cap P_{C'}, \true, \noop) \in \Gamma_\cC$,
-  which concludes the proof.
-\end{proof}
-
-\begin{lemma}
-  \label{lem:onestep}
-  Let $\cB$ be a set of components; let $A_i = (\{C_i\}, V_{A_i},
-  P_{A_i}, \Gamma_i)$, for $i = 1,2$, be two architectures
-  applicable to $\cB$, with one coordinator each, and denote
-  $P_i = P_{C_i} \cup \bigcup_{B \in \cB} P_B$.
-  Finally, let
-%
-  $
-  s_1 s_2 s
-%
-  \goesto{a, \tilde{\val{}{}}}
-%
-  s_1' s_2' s'
-  $,
-%
-  be a transition in $\semopen{(A_1 \arcomp A_2)(\cB)}$, with
-  $a \neq \emptyset$, 
-  $s, s' \in \prod_{B \in \cB} S_{\semopen{B}}$
-  and
-  $s_i, s_i' \in S_{\semopen{C_i}}$ ($i=1,2$).
-%
-  Then, for $i=1,2$, either $a \cap P_i = \emptyset$ and $s_i s=
-  s_i' s'$, or there exists a transition
-%
-  $
-  s_i s
-%
-  \goesto{a \cap P_i, \val[\doubletilde]{}{}}
-%
-  s_i' s''
-  $ 
-%
-  in $\semopen{A_i(\cB)}$, with
-  $\val[\doubletilde]{}{}$ being the restriction of
-  $\val[\tilde]{}{}$ to
-  $V_1 = V_{C_1} \cup \bigcup_{B \in \cB} V_B$ and
-  $s' \order s''$.
-\end{lemma}
-%
-\begin{proof}
-  By \defn{comp:semantics}, every semantic state consists of a
-  component state and a valuation of component variables.  Thus,
-  we have
-%
-  \[
-  (q_1, \val{}{1}, q_2, \val{}{2}, q, \val{}{})
-%
-  \goesto{a, \tilde{\val{}{}}}
-%
-  (q_1', \val[\primeit]{}{1}, q_2', \val[\primeit]{}{1}, q', \val[\primeit]{}{})
-  \,.
-  \]
-%
-  By \eq{comp:semantics} and \eq{im:int}, this implies
-  $(q_1, q_2, q) \goesto {a, G, E} (q_1', q_2', q')$, with
-%
-  $G = g \land g_1 \land g_2 \land g_b$
-  and
-  $E = e; (e_1, e_2, e_b)$,
-  where
-%    
-  \begin{mathpar}
-    g_b = \bigwedge_{B \in \supp{a} \cap \cB} g_B
-    \,,
-    \and
-    e_b = (e_B)^{B \in \supp{a} \cap \cB}
-  \end{mathpar}
-%
-  and such that $(a, g, e) \in \Gamma$ (see
-  \eq{arch:composition}) and
-%
-  \begin{align}
-    \label{eq:guard}
-    (\val{}{1}, \val{}{2}, \val{}{}) &\models G
-    \,,
-    \\
-    \label{eq:substitution}
-    (\val[\primeit]{}{1}, \val[\primeit]{}{2}, \val[\primeit]{}{})
-    &= \val[\tilde]{}{}[E]
-    \,,
-    \\
-    \label{eq:transient}
-    \valdiff{(\val{}{1}, \val{}{2}, \val{}{})}{\val[\tilde]{}{}}
-    &\subseteq \export(a)
-    \,.
-  \end{align}
-%
-  If $a \cap P_1 = \emptyset$, then $\supp{a} = \{C_2\}$ and, by
-  \eq{transient} and \defn{im}, $s_1 = s_1'$ and $s = s'$
-  (recall, \defn{im}, that, for $(a,g,e) \in \Gamma$, we have $e
-  \in \exprs{V_a}$).  Hereafter, assume $a \cap P_1 \neq
-  \emptyset$.
-
-  Denoting $P_b = \bigcup_{B \in \supp{a} \cap \cB} P_B$, we
-  have, by \eq{im:int},
-%
-  \begin{mathpar}
-    q_1 \goesto{a \cap P_{C_1}, g_1, e_1} q_1'
-    \and
-    \text{and}
-    \and
-    q \goesto{a \cap P_b, g_b, e_b} q'
-    \,.
-  \end{mathpar}
-
-  By \eq{arch:composition}, for $i=1,2$, there exist
-  $(a \cap P_{A_i}, g^i, e^i) \in \Gamma_i$,
-  such that $g = g^1 \land g^2$ and $e = e^1 \land e^2$.
-  By \eq{guard}, we have
-  $(\val{}{1}, \val{}{}) \models g^1 \land g_1 \land g_b$.
-
-  Denoting $\val[\doubletilde]{}{}$ the restriction of
-%
-  $\val[\tilde]{}{}$ to
-  $V_1 = V_{C_1} \cup \bigcup_{B \in \cB} V_B$,
-%
-  we have, by \eq{substitution} and the monotonicity of
-  expressions,
-%
-  $(\val[\primeit]{}{1}, \val[\primeit]{}{}) \order
-  \val[\doubletilde]{}{}[e^1; (e_1, e_b)]$.  Notice that all
-  variables affected by both $e^1$ and $e^2$ must necessarily
-  belong to $\bigcup_{B \in \cB} V_B$.  Hence,
-%
-  $\val[\doubletilde]{}{}[e^1; (e_1, e_b)] =
-  (\val[\primeit]{}{1}, \val[\doubleprimeit]{}{})$ with 
-  $\val[\primeit]{}{} \order \val[\doubleprimeit]{}{}$.
-
-  By \eq{comp:semantics} and \eq{im:int}, we have
-  \[
-  (q_1, \val{}{1}, q, \val{}{})
-  \goesto{a \cap P_1, \val[\doubletilde]{}{}}
-  (q_1', \val[\primeit]{}{1}, q, \val[\doubleprimeit]{}{})
-  \,.
-  \]
-\end{proof}
-
-\begin{lemma}
-  \label{lem:stepabove}
-  Consider a component $B$ and let 
-%
-  $
-  (q_1, \val{}{1})
-%
-  \goesto{a, \val[\tilde]{}{}}
-%
-  (q_2, \val{}{2})
-  $,
-%
-  be a transition in $\semopen{B}$.  For any valuation
-  $\val[\primeit]{}{1}$, such that
-  $\val{}{1} \order \val[\primeit]{}{1}$ and
-  $\valdiff{\val{}{1}}{\val[\primeit]{}{1}} \subseteq \export(a)$,
-  there exists a transition
-%
-  $
-  (q_1, \val[\primeit]{}{1})
-%
-  \goesto{a, \val[\tilde]{}{}}
-%
-  (q_2, \val{}{2})
-  $
-%
-  in $\semopen{B}$.
-\end{lemma}
-%
-\begin{proof}
-  By \eq{comp:semantics}, we have
-%
-  \begin{mathpar}
-    q_1 \goesto{a, g, e} q_2
-    \,,
-    \and
-    \val{}{1} \models g
-    \,,
-    \and
-    \val{}{2} = \val[\tilde]{}{}[e]
-    \,,
-    \and
-    \text{and}
-    \and
-    \valdiff{\val{}{1}}{\val[\tilde]{}{}} \subseteq \export(a)
-    \,.
-  \end{mathpar}
-
-  By monotonicity of guards, we deduce
-  $\val[\primeit]{}{1} \models g$.
-  For any $v \in \export(a)$,
-  $\val[\primeit]{}{1}(v) = \val{}{1}(v) = \val[\tilde]{}{}(v)$.
-  Hence, 
-  $\valdiff{\val[\primeit]{}{1}}{\val[\tilde]{}{}}
-  \subseteq \export(a)$.
-  By \eq{comp:semantics}, we conclude 
-%
-  $
-  (q_1, \val[\primeit]{}{1})
-%
-  \goesto{a, \val[\tilde]{}{}}
-%
-  (q_2, \val{}{2})
-  $.  
-\end{proof}
-
-\begin{proof}[Proof of \thm{combining}]
-  By \lem{onlyone}, we can assume that each of the two
-  architectures has only one coordinating component.  For $i =
-  1,2$, we denote $\{C_i\} = \cC_i$, $P_i = P_{C_i}
-  \cup\ \bigcup_{B \in \cB} P_B$ and $V_i = V_{C_i}
-  \cup\ \bigcup_{B \in \cB} V_B$.
-
-  The initiality of $\Phi_1 \land \Phi_2$, is trivial: both
-  $\Phi_1$ and $\Phi_2$ are initial, hence $s^0 \models \Phi_1
-  \land \Phi_2$.
-
-  Consider a path
-%
-  \[
-  s^0_1 s^0_2 s^0
-%
-  \goesto{a^1, \val[\tilde]{1}{}}
-%
-  s^1_1 s^1_2 s^1
-%
-  \goesto{a^2, \val[\tilde]{2}{}}
-  \cdots
-  \goesto{a^k, \val[\tilde]{k}{}}
-%
-  s^k_1 s^k_2 s^k
-  \]
-%
-  in $\semopen{(A_1 \arcomp A_2)(\cB)}$, where
-  $s^0,\dots,s^k \in \prod_{B \in \cB} S_{\semopen{B}}$ and
-  $s^0_i,\dots, s^k_i \in S_{\semopen{C_i}}$, for $i=1,2$.
-  We have to show that $s^k \models \Phi_1 \land \Phi_2$.
-
-  Assuming that $a^1 \cap P_1 \neq \emptyset$, by \lem{onestep},
-  there exists $s^{1\prime} \in \prod_{B \in \cB} S_{\semopen{B}}$,
-  such that
-%
-  \[
-  s^0_1 s^0
-%
-  \goesto{a^1 \cap P_1, \val[\doubletilde]{1}{}}
-%
-  s^1_1 s^{1\prime}
-  \]
-%
-  is a transition in $\semopen{A_1(\cB)}$ with
-  $\val[\doubletilde]{1}{}$ being the restriction of
-  $\val[\tilde]{1}{}$ to $V_1$ and
-  $s^1 \order s^{1\prime}$.
-%
-  By \lem{stepabove}, 
-  \[
-  s^1_1 s^1_2 s^{1\prime}
-%
-  \goesto{a^2, \val[\tilde]{2}{}}
-%
-  s^2_1 s^2_2 s^2
-  \]
-  is a transition in $\semopen{(A_1 \arcomp A_2)(\cB)}$ and,
-  therefore, 
-  \[
-  s^1_1 s^1_2 s^{1\prime}
-%
-  \goesto{a^2, \val[\tilde]{2}{}}
-%
-  s^2_1 s^2_2 s^2
-%
-  \goesto{a^3, \val[\tilde]{3}{}}
-  \cdots
-  \goesto{a^k, \val[\tilde]{k}{}}
-%
-  s^k_1 s^k_2 s^k
-  \]
-%  
-  is a path in $\semopen{(A_1 \arcomp A_2)(\cB)}$.
-%
-  Notice that, if the above assumption, $a^1 \cap P_1 \neq
-  \emptyset$, does not hold, then $s^0_1 = s^1_1$, $s^0 = s^1$
-  and we can take $s^{1\prime} = s^1$ in this latter path.
-
-  Repeating the entire argument $k-1$ times, starting with this
-  shorter path, we obtain a path
-%
-  \begin{equation}
-    \label{eq:path-in-1}
-    s^0_1 s^0
-    %
-    \goesto{a^1 \cap P_1, \val[\doubletilde]{1}{}}
-    %
-    s^1_1 s^{1\prime}
-    %
-    \goesto{a^2 \cap P_1, \val[\doubletilde]{2}{}}
-    %
-    s^2_1 s^{2\prime}
-    %
-    \goesto{a^3 \cap P_1, \val[\doubletilde]{3}{}}
-    \cdots
-    \goesto{a^k \cap P_1, \val[\doubletilde]{k}{}}
-    %
-    s^k_1 s^{k'}
-  \end{equation}
-%  
-  with $s^i \order s^{i\prime}$, for all $i \in [1,k]$.
-
-  From \eq{path-in-1}, we conclude that the state $s^k_1
-  s^{k\prime}$ is reachable in $\semopen{A_1(\cB)}$.  Since $A_1$
-  enforces $\Phi_1$ on $\cB$, this implies that $s^{k\prime}
-  \models \Phi_1$.  Since $s^k \order s^{k\prime}$, we deduce, by
-  \defn{property}, that $s^k \models \Phi_1$.
-
-  Symmetrically, $s^k \models \Phi_2$, which concludes
-  the proof.
-\end{proof}
 
@@
 \end{definition}
-\noteLH[]{}is dom and codom clear?
+\noteLH{is dom and codom clear?}
 Now we define
@@
 
+%****************************************************************
+%****************************************************************
+\appendix
+\clearpage
+
+\section{Proofs}
+
+\begin{lemma}
+  \label{lem:onlyone}
+  Let $A = (\cC, V_A, P_A, \Gamma)$ be an architecture and denote
+  by $\Gamma_\cC \bydef{=}
+%
+  \setdef{
+    (a \cap P_\cC, \true, \noop)
+  }{
+    (a, g, e) \in \Gamma
+  }$, with $P_\cC = \bigcup_{C \in \cC} P_C$,
+%  
+  the projection of $\Gamma$ onto the coordinating components of
+  $A$.  Consider the architecture $A' = (\{C'\}, V_A, P_A,
+  \Gamma)$, where $C' = \Gamma_\cC(\cC)$.  For any set of
+  components $\cB$, satisfying the conditions of
+  \defn{arch:application}, we have
+  $\semopen{A(\cB)} = \semopen{A'(\cB)}$.
+\end{lemma}
+%
+\begin{proof}
+  First of all, notice that, by \defn{im},
+  $V_{C'} = \bigcup_{C \in \cC} V_C$ and $P_{C'} = P_\cC$.
+  The conditions of \defn{arch} are satisfied and $A'$ is indeed
+  an architecture.  Furthermore, $\cB$ satisfies the conditions
+  of \defn{arch:application} \wrt $A'$.  Hence, the component
+  $A'(\cB)$ is well defined.
+
+  Clearly the state spaces, initial states and interfaces of both
+  components coincide.  Thus we only have to prove that so do the
+  transition relations.  Let us assume that
+  $\cC = C_i^{i \in I}$ and $\cB = B_j^{j \in J}$.
+  We will use $q_i, q_i'$ to denote the states of
+  $C_i$ and $q_j, q_j'$ to denote the states of $B_j$,
+  and similarly for the valuations of variables.
+
+  By \defn{comp:semantics}, a transition
+%
+  \begin{equation}
+    \label{eq:lem1:trans:sem}
+    (q_i, \val{}{i})^{i \in I} (q_j, \val{}{j})^{j \in J}
+    \goesto{a, \val[\tilde]{}{}}
+    (q_i', \val{\prime}{i})^{i \in I}
+    (q_j', \val{\prime}{j})^{j \in J}
+  \end{equation}
+%  
+  is a transition in $\semopen{A(\cB)}$ (\resp
+  $\semopen{A'(\cB)}$) iff
+%
+  \begin{equation}
+    \label{eq:lem1:trans}
+    q_i^{i \in I} q_j^{j \in J}
+    \goesto{a, G, E}
+    (q_i')^{i \in I} (q_j')^{j \in J}
+    \,,
+  \end{equation}
+%
+  is a transition in $A(\cB)$ (\resp $A'(\cB)$) and
+%
+  \begin{mathpar}
+    \val{}{i}^{i \in I} \val{}{j}^{j \in J}
+    \models G
+    \,,
+    \and
+    (\val{\prime}{i})^{i \in I} (\val{\prime}{j})^{j \in J}
+    = \val[\tilde]{}{}[E]
+    \,,
+    \and
+    \valdiff{\val{}{i}^{i \in I} \val{}{j}^{j \in J}}{
+      \val[\tilde]{}{}} \subseteq \export(a)
+    \,.   
+  \end{mathpar}
+
+  By \defn{im}, \eq{lem1:trans} is a transition in $A(\cB)$
+  iff $a \neq \emptyset$, $(a, g, e) \in \IMextend{\Gamma}{P}$,
+  where $P = \bigcup_{B \in \cB \cup \cC} P_B$, and
+  %
+  \begin{enumerate}
+  \item for $i \in I$,
+    $q_i \goesto{a \cap P_{C_i}, g_{C_i}, e_{C_i}} q_i'$
+    is a transition in $C_i$, or
+    $a \cap P_{C_i} = \emptyset$ and $q_i = q_i'$,
+    $g_{C_i} = \true$ and $e_{C_i} = \noop$\,;
+  \item for $j \in J$,
+    $q_j \goesto{a \cap P_{B_j}, g_{B_j}, e_{B_j}} q_j'$
+    is a transition in $B_j$, or
+    $a \cap P_{B_j} = \emptyset$ and $q_j = q_j'$,
+    $g_{B_j} = \true$ and $e_{B_j} = \noop$\,;
+  \item $G = g \land \bigwedge_{i \in I} g_{C_i} \land
+    \bigwedge_{j \in J} g_{B_j}$ and
+    $E = e; e_{C_i}^{i \in I}, e_{B_j}^{j \in J}$.
+  \end{enumerate}
+  %
+
+  Similarly, \eq{lem1:trans} is a transition in
+  $A'(\cB)$ iff $a \neq \emptyset$,
+  $(a, g, e) \in \IMextend{\Gamma}{P}$ and
+  %
+  \begin{enumerate}
+  \item \label{only1:coord}
+    $(q_i)^{i \in I}
+    \goesto{a \cap P_{C'}, g_{C'}, e_{C'}}
+    (q_i')^{i \in I}$ is a transition in $C'$,
+    or $a \cap P_{C'} = \emptyset$ and $q_i = q_i'$,
+    for all $i \in [1,m]$,
+    $g_{C'} = \true$ and $e_{C'} = \noop$\,;
+  \item for $j \in J$,
+    $q_j \goesto{a \cap P_{B_j}, g_{B_j}, e_{B_j}} q_j'$
+    is a transition in $B_j$, or
+    $a \cap P_{B_j} = \emptyset$ and $q_j = q_j'$,
+    $g_{B_j} = \true$, and $e_{B_j} = \noop$;
+  \item $G = g \land g_{C'} \land
+    \bigwedge_{j \in J} g_{B_j}$ and
+    $E = e; e_{C'}, e_{B_j}^{j \in J}$.
+%
+  \breakenumistart
+  Notice that, for any $i \in I$, since
+  $P_{C_i} \subseteq P_{C'}$, we have
+  $a \cap P_{C_i} = (a \cap P_{C'}) \cap P_{C_i}$.
+  Thus, if $a \cap P_{C'} \neq \emptyset$, 
+  the transition in condition~\ref{only1:coord} above is
+  present in $C'$ iff
+  $(a \cap P_{C'}, \true, \noop) \in \Gamma_\cC$ and
+  \breakenumiend
+% 
+  \item for $i \in I$,
+    $q_i \goesto{a \cap P_{C_i}, g_{C_i}, e_{C_i}} q_i'$
+    is a transition in $C_i$, or $a \cap P_{C_i} = \emptyset$
+    and $q_i = q_i'$,
+    $g_{C_i} = \true$ and $e_{C_i} = \noop$,
+  \item $g_{C'} = \bigwedge_{i \in I} g_{C_i}$ and
+    $e_{C'} = e_{C_i}^{i \in I}$.
+  \end{enumerate}
+
+  Consider $(a,g,e) \in \IMextend{\Gamma}{P}$.  By
+  \eq{im:extension}, this is equivalent to
+  $(a \cap P_A, g, e) \in \Gamma$.
+  Since $P_{C'} = P_\cC \subseteq P_A$, we have
+  $a \cap P_{C'} = a \cap P_\cC = (a \cap P_A) \cap P_\cC$.
+  Hence, this is also equivalent to
+  $(a \cap P_{C'}, \true, \noop) \in \Gamma_\cC$,
+  which concludes the proof.
+\end{proof}
+
+\begin{lemma}
+  \label{lem:onestep}
+  Let $\cB$ be a set of components; let $A_i = (\{C_i\}, V_{A_i},
+  P_{A_i}, \Gamma_i)$, for $i = 1,2$, be two architectures
+  applicable to $\cB$, with one coordinator each, and denote
+  $P_i = P_{C_i} \cup \bigcup_{B \in \cB} P_B$.
+  Finally, let
+%
+  $
+  s_1 s_2 s
+%
+  \goesto{a, \tilde{\val{}{}}}
+%
+  s_1' s_2' s'
+  $,
+%
+  be a transition in $\semopen{(A_1 \arcomp A_2)(\cB)}$, with
+  $a \neq \emptyset$, 
+  $s, s' \in \prod_{B \in \cB} S_{\semopen{B}}$
+  and
+  $s_i, s_i' \in S_{\semopen{C_i}}$ ($i=1,2$).
+%
+  Then, for $i=1,2$, either $a \cap P_i = \emptyset$ and $s_i s=
+  s_i' s'$, or there exists a transition
+%
+  $
+  s_i s
+%
+  \goesto{a \cap P_i, \val[\doubletilde]{}{}}
+%
+  s_i' s''
+  $ 
+%
+  in $\semopen{A_i(\cB)}$, with
+  $\val[\doubletilde]{}{}$ being the restriction of
+  $\val[\tilde]{}{}$ to
+  $V_1 = V_{C_1} \cup \bigcup_{B \in \cB} V_B$ and
+  $s' \order s''$.
+\end{lemma}
+%
+\begin{proof}
+  By \defn{comp:semantics}, every semantic state consists of a
+  component state and a valuation of component variables.  Thus,
+  we have
+%
+  \[
+  (q_1, \val{}{1}, q_2, \val{}{2}, q, \val{}{})
+%
+  \goesto{a, \tilde{\val{}{}}}
+%
+  (q_1', \val[\primeit]{}{1}, q_2', \val[\primeit]{}{1}, q', \val[\primeit]{}{})
+  \,.
+  \]
+%
+  By \eq{comp:semantics} and \eq{im:int}, this implies
+  $(q_1, q_2, q) \goesto {a, G, E} (q_1', q_2', q')$, with
+%
+  $G = g \land g_1 \land g_2 \land g_b$
+  and
+  $E = e; (e_1, e_2, e_b)$,
+  where
+%    
+  \begin{mathpar}
+    g_b = \bigwedge_{B \in \supp{a} \cap \cB} g_B
+    \,,
+    \and
+    e_b = e_B^{B \in \supp{a} \cap \cB}
+  \end{mathpar}
+%
+  and such that $(a, g, e) \in \Gamma$ (see
+  \eq{arch:composition}) and
+%
+  \begin{align}
+    \label{eq:guard}
+    (\val{}{1}, \val{}{2}, \val{}{}) &\models G
+    \,,
+    \\
+    \label{eq:substitution}
+    (\val[\primeit]{}{1}, \val[\primeit]{}{2}, \val[\primeit]{}{})
+    &= \val[\tilde]{}{}[E]
+    \,,
+    \\
+    \label{eq:transient}
+    \valdiff{(\val{}{1}, \val{}{2}, \val{}{})}{\val[\tilde]{}{}}
+    &\subseteq \export(a)
+    \,.
+  \end{align}
+%
+  If $a \cap P_1 = \emptyset$, then $\supp{a} = \{C_2\}$ and, by
+  \eq{transient} and \defn{im}, $s_1 = s_1'$ and $s = s'$
+  (recall, \defn{im}, that, for $(a,g,e) \in \Gamma$, we have $e
+  \in \exprs{V_a}$).  Hereafter, assume $a \cap P_1 \neq
+  \emptyset$.
+
+  Denoting $P_b = \bigcup_{B \in \supp{a} \cap \cB} P_B$, we
+  have, by \eq{im:int},
+%
+  \begin{mathpar}
+    q_1 \goesto{a \cap P_{C_1}, g_1, e_1} q_1'
+    \and
+    \text{and}
+    \and
+    q \goesto{a \cap P_b, g_b, e_b} q'
+    \,.
+  \end{mathpar}
+
+  By \eq{arch:composition}, for $i=1,2$, there exist
+  $(a \cap P_{A_i}, g^i, e^i) \in \Gamma_i$,
+  such that $g = g^1 \land g^2$ and $e = e^1 \land e^2$.
+  By \eq{guard}, we have
+  $(\val{}{1}, \val{}{}) \models g^1 \land g_1 \land g_b$.
+
+  Denoting $\val[\doubletilde]{}{}$ the restriction of
+%
+  $\val[\tilde]{}{}$ to
+  $V_1 = V_{C_1} \cup \bigcup_{B \in \cB} V_B$,
+%
+  we have, by \eq{substitution} and the monotonicity of
+  expressions,
+%
+  $(\val[\primeit]{}{1}, \val[\primeit]{}{}) \order
+  \val[\doubletilde]{}{}[e^1; (e_1, e_b)]$.  Notice that all
+  variables affected by both $e^1$ and $e^2$ must necessarily
+  belong to $\bigcup_{B \in \cB} V_B$.  Hence,
+%
+  $\val[\doubletilde]{}{}[e^1; (e_1, e_b)] =
+  (\val[\primeit]{}{1}, \val[\doubleprimeit]{}{})$ with 
+  $\val[\primeit]{}{} \order \val[\doubleprimeit]{}{}$.
+
+  By \eq{comp:semantics} and \eq{im:int}, we have
+  \[
+  (q_1, \val{}{1}, q, \val{}{})
+  \goesto{a \cap P_1, \val[\doubletilde]{}{}}
+  (q_1', \val[\primeit]{}{1}, q, \val[\doubleprimeit]{}{})
+  \,.
+  \]
+\end{proof}
+
+\begin{lemma}
+  \label{lem:stepabove}
+  Consider a component $B$ and let 
+%
+  $
+  (q_1, \val{}{1})
+%
+  \goesto{a, \val[\tilde]{}{}}
+%
+  (q_2, \val{}{2})
+  $,
+%
+  be a transition in $\semopen{B}$.  For any valuation
+  $\val[\primeit]{}{1}$, such that
+  $\val{}{1} \order \val[\primeit]{}{1}$ and
+  $\valdiff{\val{}{1}}{\val[\primeit]{}{1}} \subseteq \export(a)$,
+  there exists a transition
+%
+  $
+  (q_1, \val[\primeit]{}{1})
+%
+  \goesto{a, \val[\tilde]{}{}}
+%
+  (q_2, \val{}{2})
+  $
+%
+  in $\semopen{B}$.
+\end{lemma}
+%
+\begin{proof}
+  By \eq{comp:semantics}, we have
+%
+  \begin{mathpar}
+    q_1 \goesto{a, g, e} q_2
+    \,,
+    \and
+    \val{}{1} \models g
+    \,,
+    \and
+    \val{}{2} = \val[\tilde]{}{}[e]
+    \,,
+    \and
+    \text{and}
+    \and
+    \valdiff{\val{}{1}}{\val[\tilde]{}{}} \subseteq \export(a)
+    \,.
+  \end{mathpar}
+
+  By monotonicity of guards, we deduce
+  $\val[\primeit]{}{1} \models g$.
+  For any $v \in \export(a)$,
+  $\val[\primeit]{}{1}(v) = \val{}{1}(v) = \val[\tilde]{}{}(v)$.
+  Hence, 
+  $\valdiff{\val[\primeit]{}{1}}{\val[\tilde]{}{}}
+  \subseteq \export(a)$.
+  By \eq{comp:semantics}, we conclude 
+%
+  $
+  (q_1, \val[\primeit]{}{1})
+%
+  \goesto{a, \val[\tilde]{}{}}
+%
+  (q_2, \val{}{2})
+  $.  
+\end{proof}
+
+\begin{proof}[Proof of \thm{combining}]
+  By \lem{onlyone}, we can assume that each of the two
+  architectures has only one coordinating component.  For $i =
+  1,2$, we denote $\{C_i\} = \cC_i$, $P_i = P_{C_i}
+  \cup\ \bigcup_{B \in \cB} P_B$ and $V_i = V_{C_i}
+  \cup\ \bigcup_{B \in \cB} V_B$.
+
+  The initiality of $\Phi_1 \land \Phi_2$, is trivial: both
+  $\Phi_1$ and $\Phi_2$ are initial, hence $s^0 \models \Phi_1
+  \land \Phi_2$.
+
+  Consider a path
+%
+  \[
+  s^0_1 s^0_2 s^0
+%
+  \goesto{a^1, \val[\tilde]{1}{}}
+%
+  s^1_1 s^1_2 s^1
+%
+  \goesto{a^2, \val[\tilde]{2}{}}
+  \cdots
+  \goesto{a^k, \val[\tilde]{k}{}}
+%
+  s^k_1 s^k_2 s^k
+  \]
+%
+  in $\semopen{(A_1 \arcomp A_2)(\cB)}$, where
+  $s^0,\dots,s^k \in \prod_{B \in \cB} S_{\semopen{B}}$ and
+  $s^0_i,\dots, s^k_i \in S_{\semopen{C_i}}$, for $i=1,2$.
+  We have to show that $s^k \models \Phi_1 \land \Phi_2$.
+
+  Assuming that $a^1 \cap P_1 \neq \emptyset$, by \lem{onestep},
+  there exists $s^{1\prime} \in \prod_{B \in \cB} S_{\semopen{B}}$,
+  such that
+%
+  \[
+  s^0_1 s^0
+%
+  \goesto{a^1 \cap P_1, \val[\doubletilde]{1}{}}
+%
+  s^1_1 s^{1\prime}
+  \]
+%
+  is a transition in $\semopen{A_1(\cB)}$ with
+  $\val[\doubletilde]{1}{}$ being the restriction of
+  $\val[\tilde]{1}{}$ to $V_1$ and
+  $s^1 \order s^{1\prime}$.
+%
+  By \lem{stepabove}, 
+  \[
+  s^1_1 s^1_2 s^{1\prime}
+%
+  \goesto{a^2, \val[\tilde]{2}{}}
+%
+  s^2_1 s^2_2 s^2
+  \]
+  is a transition in $\semopen{(A_1 \arcomp A_2)(\cB)}$ and,
+  therefore, 
+  \[
+  s^1_1 s^1_2 s^{1\prime}
+%
+  \goesto{a^2, \val[\tilde]{2}{}}
+%
+  s^2_1 s^2_2 s^2
+%
+  \goesto{a^3, \val[\tilde]{3}{}}
+  \cdots
+  \goesto{a^k, \val[\tilde]{k}{}}
+%
+  s^k_1 s^k_2 s^k
+  \]
+%  
+  is a path in $\semopen{(A_1 \arcomp A_2)(\cB)}$.
+%
+  Notice that, if the above assumption, $a^1 \cap P_1 \neq
+  \emptyset$, does not hold, then $s^0_1 = s^1_1$, $s^0 = s^1$
+  and we can take $s^{1\prime} = s^1$ in this latter path.
+
+  Repeating the entire argument $k-1$ times, starting with this
+  shorter path, we obtain a path
+%
+  \begin{equation}
+    \label{eq:path-in-1}
+    s^0_1 s^0
+    %
+    \goesto{a^1 \cap P_1, \val[\doubletilde]{1}{}}
+    %
+    s^1_1 s^{1\prime}
+    %
+    \goesto{a^2 \cap P_1, \val[\doubletilde]{2}{}}
+    %
+    s^2_1 s^{2\prime}
+    %
+    \goesto{a^3 \cap P_1, \val[\doubletilde]{3}{}}
+    \cdots
+    \goesto{a^k \cap P_1, \val[\doubletilde]{k}{}}
+    %
+    s^k_1 s^{k\prime}
+  \end{equation}
+%  
+  with $s^i \order s^{i\prime}$, for all $i \in [1,k]$.
+
+  From \eq{path-in-1}, we conclude that the state $s^k_1
+  s^{k\prime}$ is reachable in $\semopen{A_1(\cB)}$.  Since $A_1$
+  enforces $\Phi_1$ on $\cB$, this implies that $s^{k\prime}
+  \models \Phi_1$.  Since $s^k \order s^{k\prime}$, we deduce, by
+  \defn{property}, that $s^k \models \Phi_1$.
+
+  Symmetrically, $s^k \models \Phi_2$, which concludes
+  the proof.
+\end{proof}
+
 \end{document}

### 2018-02-11 2018-Arch-pNets/arch-pNets.tex
Minor clean-up

@@
 
-\todoSBin{Preliminaries on the universal(?) data domain $\data$
+\noteSBin{%
+  Need preliminaries on the universal(?) data domain $\data$
   and valuations.
-
+}
+
+\noteSBin{%
 For two valuations $\val{1}{}, \val{2}{} : V \rightarrow \data$,
@@
 that are assigned different values by the two valuations.
-
+}
+
+\noteSBin{%
 To guarantee preservation of properties guards and expressions
@@
   monotonic}.  Thus, this is not really a constraint!
+
+Do we put this in the definition of expressions and guards or in
+the definitions of components and interaction models?
 }
@@
   \begin{mathpar}
-    \val{}{i}^{i \in I} \val{}{j}^{j \in J}
+    \val{i \in I}{i} \val{j \in J}{j}
     \models G
@@
     \and
-    \valdiff{\val{}{i}^{i \in I} \val{}{j}^{j \in J}}{
+    \valdiff{\val{i \in I}{i} \val{j \in J}{j}}{
       \val[\tilde]{}{}} \subseteq \export(a)

### 2018-02-12 2016-Weak-FH-Bisim/WeakBisim.tex
unification trial ...
Bisim figure

@@
 		$\vars(\alpha)\backslash \iv(\alpha)\!\subseteq\! \vars(s)$, 
-		$\vars(e_b)\!\subseteq\! \vars(s)\cup\varsigma(\alpha)$, and
-		$\forall j\!\in\! J .\,\vars(e_j)\!\subseteq\! \vars(s)\cup\varsigma(\alpha)\land 
+		$\vars(e_b)\!\subseteq\! \vars(s)\cup\vars(\alpha)$, and
+		$\forall j\!\in\! J .\,\vars(e_j)\!\subseteq\! \vars(s)\cup\vars(\alpha)\land 
 		x_j\!\in\!\vars(s')$. %,  and $s= s'\Rightarrow J=\emptyset$. 
@@
 
-  \TODO{Eric: what is ``elimination of intermediate variables ?'' it
-    transforms the predicates, so I think it is not any kind of
+  \TODO{Eric: define ``elimination of intermediate variables ?'' it
+    transforms the predicates, it is not an
     ``equivalence'' transformation, rather some sort of
-    abstraction... Define... Does it change the satisfiability ?}
+    abstraction... Does it change the satisfiability ?}
 
@@
 	\includegraphics[width=\linewidth]{XFIG/Bisim}
-	\TODO{change fig: s1,s2 $\to$ s,t. DONE we will check if it is OK. Why did we use tilde notation for R}
+	\TODO{J'ai remis $\mathcal{R}$, mais c'est un abus de notation, le $\Pred_{s,t}$ n'apparait pas dans la figure...}
 \end{minipage}
@@
 }
-
-Possible Lotos small examples:
-
-Strong bisim:\\
-1) Hiding:\\
-\centerline{hide \{g\} in a;B  ==  a; hide \{g\} in B  iff gatename(a)$\neq$g}\\
-\centerline{hide \{g\} in a;B  ==  i; hide \{g\} in B  iff gatename(a)$=$g}
-2) Disabling:\\
-\centerline{B1[>(B2[>B3) == (B1[>B2)[>b3}\\
-\centerline{(B1[>B2)[]B3 == B1[>B2}\\
-\centerline{B[>stop == B}\\
-\centerline{stop[>B == B}\\
-\centerline{exit(...)[>B == exit(...)[]B}\\
-3) Enabling:\\
-\centerline{B1>>(B2>>B3) == (B1>>B2)>>b3}\\
-\centerline{B>>stop == B|||stop}\\
-\centerline{stop>>B == stop}\\
-\centerline{exit>>B == i;B}\\
-4) Choice:\\
-\centerline{B1[](B2[]B3) == (B1[]B2)[]b3}\\
-\centerline{B1[]B2 == B2[]B1}\\
-\centerline{B[]stop == B}\\
-\centerline{B[]B == B}\\
-
-5) Others:\\
-\centerline{B1|[]|B2 == B1|||B2}\\
-
-Weak congruence:\\
-\centerline{a;i;B == a;B}\\
-\centerline{B[]i;B == i;B}\\
-and many others, often not easy to express without syntax for set operations,
-like e.g.:
-\centerline{}
-
-Weak equivalence:\\
-\centerline{i;B == B}
 
@@
   \newpage
-
+\section{Examples of Lotos laws}
+Possible Lotos small examples:
+
+Strong bisim:\\
+1) Hiding:\\
+\centerline{hide \{g\} in a;B  ==  a; hide \{g\} in B  iff gatename(a)$\neq$g}\\
+\centerline{hide \{g\} in a;B  ==  i; hide \{g\} in B  iff gatename(a)$=$g}
+2) Disabling:\\
+\centerline{B1[>(B2[>B3) == (B1[>B2)[>b3}\\
+\centerline{(B1[>B2)[]B3 == B1[>B2}\\
+\centerline{B[>stop == B}\\
+\centerline{stop[>B == B}\\
+\centerline{exit(...)[>B == exit(...)[]B}\\
+3) Enabling:\\
+\centerline{B1>>(B2>>B3) == (B1>>B2)>>b3}\\
+\centerline{B>>stop == B|||stop}\\
+\centerline{stop>>B == stop}\\
+\centerline{exit>>B == i;B}\\
+4) Choice:\\
+\centerline{B1[](B2[]B3) == (B1[]B2)[]b3}\\
+\centerline{B1[]B2 == B2[]B1}\\
+\centerline{B[]stop == B}\\
+\centerline{B[]B == B}\\
+
+5) Others:\\
+\centerline{B1|[]|B2 == B1|||B2}\\
+
+Weak congruence:\\
+\centerline{a;i;B == a;B}\\
+\centerline{B[]i;B == i;B}\\
+and many others, often not easy to express without syntax for set operations,
+like e.g.:
+\centerline{}
+
+Weak equivalence:\\
+\centerline{i;B == B}
+
+\newpage
   \section{Running example: Hierarchical Broadcast}

### 2018-02-12 2016-Weak-FH-Bisim/WeakBisim.tex
added a todo
removed magical op new def of leaves new tr2 took guard into account until page 20

@@
 
-\LUDO{introduce magic op}
-$\CreateISet{a}{i}$ creates a single entry indexed set $(i\mapsto a)$ \emph{but only if 
-$a$ is not already an indexed set.}
+%\LUDO{introduce magic op}
+%$\CreateISet{a}{i}$ creates a single entry indexed set $(i\mapsto a)$ \emph{but only if 
+%$a$ is not already an indexed set.}
 
@@
 \[\begin{array}{l}
-\Leaves(\mylangle S,s_0, \to\myrangle) \!=\!\mylangle S,s_0, \to\myrangle\\
+\Leaves(\mylangle S,s_0, \to\myrangle) \!=\!\{\mylangle S,s_0, \to\myrangle\}\\
 \Leaves(\mylangle \pNet_i^{i\in I}\!,%Sort_j^{j\in J}
 \overline{\Sort}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \biguplus_{i\in 
-I}\CreateISet{\Leaves(\pNet_i)}{i} }
+I}\Leaves(\pNet_i)\uplus\{i\mapsto \pNet_i|\pNet_i=\pLTS\}}
 \end{array}\]
@@
 \label{section:op-semantics}
+
+\TODO{update pred with guards}
 
@@
   \triangleright| \forall i\in L. s_i \in S_i\}$.
-\TODO{this definition is not valid because L is undefined and leaves only exist for pNets 
--> REMOVE? this would mean that a pNet is not a pLTS ...}
 A pLTS being its own single leave:
@@
 Let
-$\mylangle\overline{\pNet},\overline{\Sort},\symb{SV}_k^{k\in K} \myrangle$
-be a pNet. Consider a synchronisation vector $SV_k$, for $k\in K$. We define a
+$\mylangle\overline{\pNet},\overline{\Sort},\overline{\symb{SV}}\myrangle$
+be a pNet. Consider a synchronisation vector $\symb{SV}\in \overline{\symb{SV}}$. We 
+define a
 predicate $\Pred$ relating
 the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
-\[\Pred_{\symb{sv}}(SV_k, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow \bigg(
+\[\Pred_{\symb{sv}}(SV, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow \bigg(
 \begin{array}{l}
 \exists {(a'_i)}^{i\in I},
-{(b'_j)}^{j\in J},v'.\, SV_k={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v'
+{(b'_j)}^{j\in J},v'.\, SV={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v' | g
 \\~~\land
-\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v'
+\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v' \land g
 \end{array} \bigg)\]
+\LUDO{Is and g sufficient? I would say yes}
 
@@
 	synchronisation vector.
-	\LUDO{now with the magical operator ... $s_m$ and $s_m'$ are a bit ill-typed terms. 
-	Not very happy of the new rule}
+	\LUDO{now with two cases of induction} \LUDO{Why I'm and not Im?}
 	\begin{description}
@@
     $\inferrule
-    {k\!\in\! K \\ SV\!\!= \!{\tt clone}(SV_k) \!=\! \alpha_m^{m \in I_k\uplus J_k} \!\to\! 
-    \alpha'_k \\
-    	Leaves(p) \!=\! \pLTS_l^{l\in L} \\    	
-    	\forall m\in I_k.
-    	\pNet_m \models
-    	\inferrule*[myfraction=\reddottedrule]
+    {k\!\in\! K \\SV_k \!=\! \alpha_m^{m \in I\uplus J} \!\to\! 
+    \alpha' |g \\
+    	Leaves(\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in 
+    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \\    	
+    	\forall m\!\!\in\!\! I. 	
+    {\left(\begin{array}{l}
+	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
     	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
     	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
+    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
+    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
+		{ \pNet_m 
+    	 \models
+    	\inferrule*[myfraction=\reddottedrule]
+    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
     	{\ostate{s_m} \OTarrow {v_m}
-    		\ostate{s_m'}}
+    		\ostate{s_m'}} \land I'_m=\{m\} \land J'_m=\emptyset}
+\end{array}\right)}\\
     	%\land
     	%Leaves(\pNet_m) = \overline{\pLTS}^{L_k})  	
-    	\\\forall m\in I_k. \CreateISet{s_m}{i}=s_{i}^{i \in L_m} \\
-		\forall m\in I_k. \CreateISet{s_m'}{i}=(s_i^\prime)^{i\in L_m} \\
-    	I' = \biguplus_{m\in I_k}\!\! I_m'
-    	\\ J' = \biguplus_{m\in I_k}\!\! J'_m \uplus J_k 	\\
-    	\Pred = \bigwedge_{m\in I_k}\!\! \Pred_m \land
-    	\Pred_{\symb{sv}}(SV,a_i^{i\in I_k},b_j^{j\in J_k},v)\\
-    	\forall j\!\!\in\!\! J_k. {\tt 
-    		fresh}(b_j) \\ {\tt fresh}(v) \\ 
-    	\forall i\in
-    	L\backslash I'.\,s'_i=s_i 
+     J' = \biguplus_{m\in I}\!\! J'_m \uplus J 	\\
+    	\Pred = \bigwedge_{m\in I}\!\! \Pred_m \land
+    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in I},b_j^{j\in J},v)\\ 
+    		I' = \biguplus_{m\in I}\!\! I_m'
+    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
+    {\tt fresh}(\alpha_m,\alpha',b_j,v) 
     }
@@
     $
-
 	\medskip
@@
 \begin{lemma}[OT decomposition]\label{lem-decompose} 
-	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose:
+	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
+	lemma imply that $Q$ is 
+	not a \pLTS\ but a similar lemma can be proven for a pLTS $Q$}:
 	\[ P[Q]_{j_0}  
@@
    \begin{small}\begin{proof}
-       Consider each premise of the open transition (as constructed by rule TR2 in Definition~\ref{def:operationalSemantics}). 
+       Consider each premise of the open transition (as constructed by rule TR2 in 
+       Definition~\ref{def:operationalSemantics}). 
+	\begin{description}
+		\item[{\bf Tr2:}]
+	\end{description}
+
+	\noindent
+    $\inferrule
+    {k\!\in\! K \\SV_k \!=\! \alpha_m^{m \in I\uplus J} \!\to\! 
+    \alpha' |g \\
+    	Leaves(\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in 
+    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \\    	
+    	\forall m\!\!\in\!\! I. 	
+    {\left(\begin{array}{l}
+	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
+    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
+    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
+    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
+    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
+		{ \pNet_m 
+    	 \models
+    	\inferrule*[myfraction=\reddottedrule]
+    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
+    	{\ostate{s_m} \OTarrow {v_m}
+    		\ostate{s_m'}} \land I'_m=\{m\} \land J'_m=\emptyset}
+\end{array}\right)}\\
+    	%\land
+    	%Leaves(\pNet_m) = \overline{\pLTS}^{L_k})  	
+     J' = \biguplus_{m\in I}\!\! J'_m \uplus J 	\\
+    	\Pred = \bigwedge_{m\in I}\!\! \Pred_m \land
+    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in I},b_j^{j\in J},v)\\ 
+    		I' = \biguplus_{m\in I}\!\! I_m'
+    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
+    {\tt fresh}(\alpha_m,\alpha',b_j,v) 
+    }
+    {\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
+    	\models
+    	{\inferrule*[myfraction=\reddottedrule]
+    		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I^\prime},
+    		\{\xrightarrow{b_j}_j\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_k} 
+    		\Post_m}
+    		{\ostate{s_i^{i\in L}} \OTarrow {v}
+    			\ostate{(s_i^\prime)^{i\in L}}}
+    	}
+    }
+    $
+	\medskip
+
 We know each premise is true for $P[Q]_{j_0}$ and try to prove the equivalent premise for 
@@
 $j_0$ passes from 
-the set of subnets to the set of holes). Then $SV=clone(\alpha_j^{j\in I_k\uplus\{j_0\}\uplus 
-J_k})$. $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$. 
-\TODO{Revoir la def des leaves set ou multisets}
-
-Now focus on OTs of the subnets\footnotemark[\thefootnote]:\\[-2ex]
-\[\forall m\in I_k\cup \{j_0\}.
-\pNet_m \models
+the set of subnets to the set of holes). 
+%Then $SV=clone(\alpha_j^{j\in I_k\uplus\{j_0\}\uplus J_k})$.
+We have $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$.
+
+Now focus on OTs of the subnets. For each $m\in I\cup \{j_0\}$ we have one of the two 
+following OT\footnotemark[\thefootnote]:\\[-2ex]
+\[
+\pNet_m \models\inferrule*[myfraction=\reddottedrule]
+    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
+    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
+    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
+    		\ostate{(s_i^\prime)^{i\in L_m}}}\]
+Or
+\[{ \pNet_m 
+    	 \models
     	\inferrule*[myfraction=\reddottedrule]
-{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m},
-	\{\xrightarrow{b_{j}}_j\}^{j\in J_m}, \Pred_m, \Post_m}
-{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
-	\ostate{s_{i}'^{\, i \in L_m}}}\]
-Only elements of $I_k$ are useful to assert the premise for reduction of $P$; the last 
+    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
+    	{\ostate{s_m} \OTarrow {v_m}
+    		\ostate{s_m'}} \land I'_m=\{m\} \land J'_m=\emptyset}\]
+
+Only elements of $I$ are useful to assert the premise for reduction of $P$; the last 
 one ensures (note that $Q$ is at place $j_0$, and by definition of the open transition 
-for $P[Q]_{j_0}$, $I_{j_0}=I\cap L_Q$, 
-$L_{j_0}=L_Q$):\\[-2ex]
+for $P[Q]_{j_0}$, $I'_{j_0}=I\cap L_Q$, 
+$L_{j_0}=L_Q$, and $J_{j_0}=	J\cap\Holes(Q)$):\\[-2ex]
 	\[Q\models{\inferrule*[myfraction=\reddottedrule]
@@
 		{\ostate{s_i^{i\in L_Q}} \OTarrow {v_{j_0}}
-			\ostate{s_i'^{\, i\in L_Q}}}
+			\ostate{(s_i')^{\, i\in L_Q}}}
 	}\]
-\TODO{We need to add: Note that $J_{j_0}=	J\cap\Holes(Q)$ this is a direct consequence of Tr2??}
-
-This already ensures the second part of the conclusion if we 
-choose\footnotemark[\thefootnote]  $v_Q=v_{j_0}$ ($\Pred\,''= \Pred_{j_0}$). Now let $I'= 
-\biguplus I'_m=I\setminus L_Q$, $J'=\biguplus J'_m\uplus J_k 
+
+This already ensures the second part of the conclusion of the lemma, i.e. the OT for $Q$ 
+if we 
+choose\footnotemark[\thefootnote]  $v_Q=v_{j_0}$ ($\Pred\,''= \Pred_{j_0}$). Considering 
+the OT of $P$ let $I'= 
+\biguplus I'_m=I\setminus L_Q$, $J'=\biguplus J'_m\uplus J
 \uplus\{j_0\}=J\setminus\Holes(Q)\uplus \{j_0\}$;  the predicate is 
-$\Pred\,'=\bigwedge_{m\in I_k}\Pred_m 
-\land \Pred(SV,a_i^{i\in I_k},b_j^{j\in J_k\cup \{j_0\}},v)$
-where\footnotemark[\thefootnote] $\Pred(SV,a_i^{i\in I_k},b_j^{j\in 
-J_k},v)\Leftrightarrow 
-\forall i\in I_k.\, \alpha_i=a_i\land \forall j \in J_k\cup \{j_0\}.\, \alpha_j=b_j \land 
-v=\alpha'_k 
+$\Pred\,'=\bigwedge_{m\in I_k}\Pred_m  \land \Pred_{\symb{sv}}(SV_k,v_m^{m\in 
+I},b_j^{j\in J\cup \{j_0\}},v)$
+where\footnotemark[\thefootnote] $\Pred_{\symb{sv}}(SV_k,v_m^{m\in I},b_j^{j\in J\cup 
+\{j_0\}},v)\Leftrightarrow 
+\forall i\in I_k.\, \alpha_i=a_i\land \forall j \in J\cup \{j_0\}.\, \alpha_j=b_j \land 
+v=\alpha'
 $. Modulo renaming of fresh variables, this is identical to the predicate that occurs in 

### 2018-02-12 2018-Arch-pNets/arch-pNets.tex
clean up macros and pushed semantics (improved) to the archi paper

@@
 inductively as:
-\noteLH{Not very nice but at least of the right kind for the definition of composition}
 \[\begin{array}{l}
-\Leaves(\mylangle S,s_0, \to\myrangle) \!=\!\emptyset\\
+\Leaves(\mylangle S,s_0, \to\myrangle) \!=\!\{\mylangle S,s_0, \to\myrangle\}\\
 \Leaves(\mylangle \pNet_i^{i\in I}\!,%Sort_j^{j\in J}
 \overline{\Sort}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \biguplus_{i\in 
-I}\Leaves(\pNet_i)\uplus\{i\mapsto \pNet_i|\pNet_i=\mylangle S,s_0, \to\myrangle\}}
+I}\Leaves(\pNet_i)\uplus\{i\mapsto \pNet_i|\pNet_i=\pLTS\}}
 \end{array}\]
@@
 is said to be \emph{open}.
+
+\subsection{Operational Semantics for Open pNets}
+\label{section:op-semantics}
+
+\noteLH{a pred is a g a post is a e}
+The semantics of open pNets will be defined  as an open automaton. An open
+automaton is an automaton where each transition composes transitions of several LTSs with
+action of some holes, the transition occurs if some predicates hold, and can involve a 
+set of state modifications.
+%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
+%different 
+%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
+\begin{definition}[Open transitions]
+	\label{def:OpenTransitions}
+	An \emph{open transition} over a set  $(S_i,s_{0 i}, \rightarrow_i)^{i\in
+	I}$ of LTSs, a
+	set $J$ of holes with sorts $\Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is 
+	a structure of the form:	
+	\begin{mathpar}
+	\inferrule*[myfraction=\reddottedrule]
+	{\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
+		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred, \Post}
+	{s \OTarrow {v}s'}
+	\end{mathpar}
+	Where $s, s'\in\mathcal{S}$ and for all
+        $i\in I$, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the
+	LTS $(S_i,s_{0 i}, \rightarrow_i)$, and $\xrightarrow{b_j}_j$
+        is a transition of the hole $j$, for any action $b_j$ in the
+        sort $\Sort_j$. $v$ is a variable denoting the resulting action
+        of this open transition. \Pred\ is a predicate 
+	over the different variables of the
+	terms, labels, and states $s_i$, $b_j$, $s$, $v$. \Post\ is a set of equations that 
+	hold \emph{after the open transition}, they are represented as a substitution of the 
+	form $\{x_k\gets e_k\}^{k\in K}$ 
+	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
+	variables of the open transition.
+\end{definition}
+
+\begin{example}\emph{An open-transition.}
+  \label{OT:enable-composed}
+  The \texttt{EnableCompL} pNet of Fig. \ref{schema:enable-composed} has 2 controllers 
+  and 2 holes. One of its possible open-transition is:
+
+ \smallskip
+ $  OT_2  = \openrule{
+                       0 \xrightarrow{\delta}_{C_3} 1 ~~
+                            0 \xrightarrow{l}_{C_4} 0  ~~                 
+                            \xrightarrow{\delta(x4)}_P ~~
+                            \xrightarrow{accept(x4)}_Q 
+                      }
+  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
+    {A1_0 \OTarrow{\underline{\delta(x4)}} A1_1}
+  $
+\end{example}
+
+\begin{definition}[Open automaton]
+	\label{def:open-automaton}
+	An \emph{open automaton} is a structure\\ $A =
+	<\LTS_i^{i\in I},J,\mathcal{S},s_0,\mathcal{T}>$ where:
+	\begin{itemize}
+		\item[$\bullet$]  $I$ and $J$ are  sets of indices,
+		\item[$\bullet$]  $\LTS_i^{i\in I}$ is a family of LTSs,
+		\item[$\bullet$]   $\mathcal{S}$ is a set of states and $s_0$ an initial state
+		among $\mathcal{S}$,
+		\item[$\bullet$] $\mathcal{T}$ is a set of open transitions and for each
+		$t\in \mathcal{T}$ there exist $I'$, $J'$ with $I'\subseteq I$, $J'
+		\subseteq J$, such that $t$ is an open transition over $\LTS_i^{i\in I'}$, $J'$,
+		and  $\mathcal{S}$.
+
+	\end{itemize}
+\end{definition}
+
+%
+%Then the semantics of a pNet is characterized by a set of {\em open
+%transitions}, where the hypotheses on process parameters are
+%replaced by 1) transitions of the pLTSs at the leaves, and 2) formal
+%hypotheses on the transitions of the holes. A {\em predicate} is used
+%to relate the parameters and names appearing in the actions of the
+%leaves and the holes involved in the rules, but also appearing in  the resulting action.
+
+We define states of open pNets as tuples of states, where we denote tuples
+in structured states as $\triangleleft\ldots\triangleright$ for distinguishing tuple 
+states from other tuples.
+\begin{definition}[States of open pNets]\label{def-states}
+  A state of an open pNet is a tuple (not necessarily finite) of the
+  states of its leaves.
+
+  For any pNet p, let $\Leaves(p) = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be 
+  the set of pLTS at its leaves,
+  then $States(p) = \{\triangleleft s_i^{i\in L}
+  \triangleright| \forall i\in L. s_i \in S_i\}$.
+A pLTS being its own single leave:
+  $States(\mylangle S,s_0, \to\myrangle) = \{\triangleleft s \triangleright| s \in S\}$.
+
+The initial state is defined as:
+$InitState(p) = \triangleleft {{s_i}_0}^{i\in L}  \triangleright$.
+\end{definition}
+
+%% \begin{example} \emph{State of a pNet}
+%%   The states of pNet \texttt{EnableCompL} are:
+%%   $\triangleleft 00 \triangleright, \triangleleft 10 \triangleright, \triangleleft 11 
+%%\triangleright$
+%% \end{example}
+
+\paragraph{Predicates:}
+Let
+$\mylangle\overline{\pNet},\overline{\Sort},\overline{\symb{SV}}\myrangle$
+be a pNet. Consider a synchronisation vector $\symb{SV}\in \overline{\symb{SV}}$. We 
+define a
+predicate $\Pred$ relating
+the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
+\[\Pred_{\symb{sv}}(SV, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow \bigg(
+\begin{array}{l}
+\exists {(a'_i)}^{i\in I},
+{(b'_j)}^{j\in J},v'.\, SV={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v' | g
+\\~~\land
+\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v' \land g
+\end{array} \bigg)\]
+\noteLH{Is and g sufficient? I would say yes}
+
+Somehow, this predicate entails a verification of satisfiability in the sense that if the 
+predicate $\Pred_{\symb{sv}}$ is not satisfiable, then the transition associated with the 
+synchronisation will not occur in the considered state.
+
+In any other case (if the action families do not match or if there is no valuation of
+variables such that the above formula can be ensured) the predicate is undefined.
+
+This definition is not constructive but it is easy to build the predicate constructively
+by brute-force unification of the sub-pNets
+actions with the corresponding vector actions, possibly followed by a simplification
+step.
+
+We build the semantics of open pNets as an open automaton where LTSs are the pLTSs at
+the leaves of the pNet structure, and the states are given by 
+Definition~\ref{def-states}. The open transitions first
+ project the global state into states of the leaves, then apply
+pLTS transitions on these states, and compose them with the sort of the holes. %The pNet
+%structure does not appear in the open-automaton, only the
+%set of Holes and the set of Leaves.
+The semantics   regularly instantiates \emph{fresh} variables, and uses a
+\emph{clone} operator that clones a term replacing each variable with a
+fresh one.
+
+\begin{definition}[Operational semantics of open pNets]
+	\label{def:operationalSemantics}
+	The semantics of a pNet $p$ is an open automaton $A = 
+	<Leaves(p),Holes(p),States(p),InitState(p),
+	\mathcal{T}>$ where $\mathcal{T}$ is the smallest set of open transitions		
+	satisfying the rules below:
+%	\begin{itemize}
+%		\item $J$ is the set of holes: $Holes(p)= J$. 
+		%  \item $\overline{L}^L = Leaves(p), \overline{H}^J = Holes(p)$
+%		\item ${\mathcal{S}} = States(p)$ and $s_0 = InitState(p)$
+%		\item $\mathcal{T}$ is the smallest set of open transitions		satisfying the 
+%rules below:
+%	\end{itemize}
+
+	%% \TODO{ We should be careful here: after (re) reading "Huimin
+	%% 	Lin, 'Symbolic Transition Systems with Assignements', Concur'96" I
+	%% 	think handling assignments is not trivial, even for comparisons of pLTSs. }
+
+	The rule for a pLTS  checks that the guard 
+	is verified and transforms assignments into post-conditions:
+
+	\begin{description}
+		\item[{\bf Tr1:}]
+		$\inferrule
+		{ s \xrightarrow{\langle \alpha,~g,~e\rangle} s'\in \to  }
+		{ \mylangle  S,s_0, \to \myrangle
+			\models
+			\inferrule*[myfraction=\reddottedrule]
+			{\{s \xrightarrow{\alpha} s'\} ,\emptyset ,
+			g,e}
+			{\ostate{s} \OTarrow{\alpha} \ostate{s'}}
+		}$
+	\end{description}
+%	Note that this note is greatly simplified by the fact that variables are local to 
+%	thread; introducing global state variables or accepting loops to the same 
+%	state would 
+%	require to reason 
+%	on the scope of 
+%	each variables, and to introduce additional variables to handle the several occurence 
+%	of the same pLTS variable in the predicates. Indeed the constraints on pLTS 
+%	transitions 
+%	ensure that the same variable never appears both on the left and on the right of the 
+%	equations of a predicate.
+
+	The second rule deals with pNet nodes: for each possible
+	synchronisation vector applicable to the rule subject, the premisses
+	include one {\em open transition} for each sub-pNet involved, one possible
+	{\em action} for each Hole involved, and the predicate relating these
+	with the resulting action of the vector.
+	A key to understand this rule is that the open transitions are
+	expressed in terms of the leaves and holes of the pNet structure,
+	i.e. a flatten view of the pNet: e.g. $L$ is the index set of the
+	Leaves, $L_m$ the index set of the leaves of one subnet indexed $m$, so all $L_m$
+	are disjoint subsets of $L$. Thus the states in the open transitions,
+	at each level, are tuples including states of all the
+	leaves of the pNet, not only those involved in the chosen
+	synchronisation vector.
+	\begin{description}
+		\item[{\bf Tr2:}]
+	\end{description}
+
+	\noindent
+    $\inferrule
+    {k\!\in\! K \\SV_k \!=\! \alpha_m^{m \in I\uplus J} \!\to\! 
+    \alpha' |g \\
+    	Leaves(\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in 
+    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \\    	
+    	\forall m\!\!\in\!\! I. 	
+    {\left(\begin{array}{l}
+	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
+    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
+    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
+    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
+    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
+		{ \pNet_m 
+    	 \models
+    	\inferrule*[myfraction=\reddottedrule]
+    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
+    	{\ostate{s_m} \OTarrow {v_m}
+    		\ostate{s_m'}} \land I'_m=\{m\} \land J'_m=\emptyset}
+\end{array}\right)}\\
+    	%\land
+    	%Leaves(\pNet_m) = \overline{\pLTS}^{L_k})  	
+     J' = \biguplus_{m\in I}\!\! J'_m \uplus J 	\\
+    	\Pred = \bigwedge_{m\in I}\!\! \Pred_m \land
+    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in I},b_j^{j\in J},v)\\ 
+    		I' = \biguplus_{m\in I}\!\! I_m'
+    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
+    {\tt fresh}(\alpha_m,\alpha',b_j,v) 
+    }
+    {\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
+    	\models
+    	{\inferrule*[myfraction=\reddottedrule]
+    		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I^\prime},
+    		\{\xrightarrow{b_j}_j\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_k} 
+    		\Post_m}
+    		{\ostate{s_i^{i\in L}} \OTarrow {v}
+    			\ostate{(s_i^\prime)^{i\in L}}}
+    	}
+    }
+    $
+	\medskip
+%        \TODO{may be explain how $\Pred(SV,a_i^{i\in I_k},b_j^{j\in
+%            J_k},v)$ is built ? You mean more than what is written on previous page????}
+	%%    \TODO{I have tentatively added the sort constraint on hole actions, that was
+	%%not included in the first version... I'm unsure whether this is the best place to
+	%%include it, because it may change the decidability conditions on predicates}
+
+\end{definition}
 

### 2018-02-13 2018-Arch-pNets/arch-pNets.tex
Moved notations to a new Section 2 'Preliminaries'; revised and added data and valuations.

@@
 \newcommand{\Ludo}{\\\hfill\mdash Ludo}
-\newcommand{\noteLH}[2][color=blue!40, size=\tiny]{\todo[#1]{{#2}\Ludo}}
-\newcommand{\noteLHin}[2][inline,color=blue!40]{\todo[#1]{{#2}\Ludo}}
-\newcommand{\todoLH}[2][color=blue!40, size=\tiny]{\todo[#1]{\textbf{To-do Ludo:} {#2}}}
-\newcommand{\todoLHin}[2][inline,color=blue!40]{\todo[#1]{\textbf{To-do Ludo: } {#2}}}
+\newcommand{\noteLH}[2][color=orange!40, size=\tiny]{\todo[#1]{{#2}\Ludo}}
+\newcommand{\noteLHin}[2][inline,color=orange!40]{\todo[#1]{{#2}\Ludo}}
+\newcommand{\todoLH}[2][color=orange!40, size=\tiny]{\todo[#1]{\textbf{To-do Ludo:} {#2}}}
+\newcommand{\todoLHin}[2][inline,color=orange!40]{\todo[#1]{\textbf{To-do Ludo: } {#2}}}
 
 \newcommand{\noteIn}[2][inline,color=black!20]{\todo[#1]{{#2}}}
+
+\newcommand{\add}[2][Added]{\todo[color=blue!20, size=\tiny]{#1}{\color{blue}#2}}
+%% \newcommand{\remove}[2][Removed]{\todo[color=red!20, size=\tiny]{#1}}
+\newcommand{\remove}[2][Removed]{\todo[color=red!20, size=\tiny]{#1}{\color{red}\st{#2}}}
+%% \newcommand{\replace}[3][Replaced]{\todo[color=blue!20, size=\tiny]{#1}{\color{blue}#3}}
+\newcommand{\replace}[3][Replaced]{\todo[color=blue!20, size=\tiny]{#1}{\color{blue}#3}{\color{red}\st{#2}}}
+
+\newcommand{\addSB}[1]{\add[Added by Simon]{#1}}
+\newcommand{\removeSB}[1]{\remove[Removed by Simon]{#1}}
+\newcommand{\replaceSB}[2]{\replace[Replaced by Simon]{#1}{#2}}
 
@@
 \newcommand{\cA}{\ensuremath{\mathcal{A}}}
-\newcommand{\bB}{\ensuremath{\mathbf{B}}}
+\newcommand{\fA}{\ensuremath{\mathsf{A}}}
+\newcommand{\sA}{\ensuremath{\mathbb{A}}}
 \newcommand{\cB}{\ensuremath{\mathcal{B}}}
+\newcommand{\fB}{\ensuremath{\mathsf{B}}}
 \newcommand{\sB}{\ensuremath{\mathbb{B}}}
@@
 
+\newcommand{\ordbool}{\ensuremath{\sB^{<}}}
 \newcommand{\data}{\ensuremath{\sD}}
-\newcommand{\guards}[1]{\ensuremath{\sB_{#1}}}
+\newcommand{\signature}{\ensuremath{\Sigma}}
+\newcommand{\variables}{\ensuremath{\cV}}
+\newcommand{\Talg}{\ensuremath{\cT_{\signature,\variables}}}
+\newcommand{\actions}[1]{\ensuremath{\cA_{#1}}}
+\newcommand{\guards}[1]{\ensuremath{\ordbool_{#1}}}
 \newcommand{\exprs}[1]{\ensuremath{\sE_{#1}}}
-\newcommand{\valuations}[1]{\ensuremath{\sV_{#1}}}
-\newcommand{\val}[3][]{%
-  \ensuremath{#1{\sigma}^{#2}_{#3}}%
-}
+\newcommand{\assigns}[1]{\ensuremath{\sA_{#1}}}
+\newcommand{\valuations}[1]{\ensuremath{\data^{#1}}}
+\newcommand{\val}[3][]{\ensuremath{#1{\sigma}^{#2}_{#3}}}
+
 \newcommand{\primeit}[1]{#1'}
@@
 
-\noteSBin{%
-  Need preliminaries on the universal(?) data domain $\data$
-  and valuations.
-}
-
-\noteSBin{%
-For two valuations $\val{1}{}, \val{2}{} : V \rightarrow \data$,
-we denote \[\valdiff{\val{1}{}}{\val{2}{}} \bydef{=} \setdefb{v
-  \in V}{\val{1}{}(v) \neq \val{2}{}(v)}\] the set of variables
-that are assigned different values by the two valuations.
-}
+%****************************************************************
+%****************************************************************
+
+\section{Preliminaries}
+\label{secn:preliminaries}
+
+%****************************************************************
+
+\subsection{Notations}
+\label{secn:notations}
+
+We extensively use \replaceSB{indexed structures
+over some countable indexed sets, which are equivalent to mappings over
+the countable set. }{structures indexed over some finite or countable sets of indices, which can be equivalently defined as mappings over such index sets. }% . The indexes will usually be
+% integers, bounded or not. Such an indexed family is
+%denoted
+%follows:
+\addSB{Thus, }
+$a_i^{i\in I}$
+%, or equivalently  $(i\mapsto a_i)^{i\in I}$
+denotes a family of elements $a_i$ indexed over the
+set $I$. % Such a family
+% is equivalent to the mapping $(i\mapsto a_i)^{i\in I}$.
+% To specify the set over which the structure is indexed,
+% indexed structures are always denoted with an exponent of the form $i\in I$
+% (arithmetic only appears in the indexes if necessary).
+\replaceSB{$a_i^{i\in I}$ }{This notation }defines both $I$ the set over which the family is
+indexed (called \emph{range}), and $a_i$ the elements of the family.
+E.g., $a^{i\in\{3\}}$ is the mapping with a single entry $a$ at index
+$3$ ; abbreviated $(3\mapsto a)$ in the following.
+When this is not
+ambiguous, we shall use notations for sets, and typically write
+``indexed set over I''\replaceSB{ when}{, even though} formally we should speak of multisets; and
+write $x\in a_i^{i\in I}$ to mean $\exists i\in I.\, x=a_i$.  An empty
+family is denoted $\emptyset$. \replaceSB{
+We denote classically with an overline -- $\overline{a}$ -- a family when the indexing set 
+is
+not meaningful.}{We use a classical overline notation, \eg $\overline{a}$, for a family, where the indexing set is irrelevant} \replaceSB{$\uplus$ is }{Finally, we use $\uplus$ to denote }the disjoint union on
+indexed sets.
+
+\noteIn{states looks ok, but initial state is $s_0$ in pNet and not in archi : $s^0$.  Exponent 
+position was removed from pNet because we found it complex with indexed set notation but 
+could be ok.
+\Ludo
+
+I am using exponent notation for ``modifiers'', reserving\mdash
+as much as possible\mdash index notation for enumeration.  I
+think this can be solved, where necessary, by using parentheses,
+\eg $(s^0_i)^{i \in I}$
+\Simon
+}
+
+%****************************************************************
+
+\subsection{Term algebra}
+\label{secn:terms}
+
+\todoLHin{Remove term algebra or simplify?}
+\todoLHin{universal domain $\implies$ remove sort}
+\todoLHin{replace assignments by $e_i$
+
+  In fact, in the pNet action terms, you need expressions, not
+  assignements.  Therefore assuming that all expressions are
+  assignments will not work, so the right approach is to have
+  expressions (for pNets) and assignments (for BIP) separately.
+  \Simon
+%
+}
+
+\noteSBin{In Archi we have $a$, whereas in pNets we have $\alpha$, where, approximately $\alpha = 
+a(x_1..x_n)$, except that $a$ is port name in archi and action name in pNets.
+Is this true? can we unify better? or is it sufficient?
+\Ludo
+
+$a$ is a set of ports, but otherwise, yes, this is true.  I think
+this is coherent, since, in archi, we have the ``interaction
+part'', \ie only ports, plus the data part, \ie variables,
+guards, expressions.  In pNets, these are combined.  So, it seems
+ok that notations differ\mdash ``uniformisation'' will be
+achieved by encoding archi $\rightarrow$ pNets.
+}
+
+\replaceSB{Our models rely }{The pNet model in \secn{pNets} relies }on a notion of parameterised actions, that are
+symbolic expressions using data types and variables. As \replaceSB{our model aims }{we aim }at encoding the low-level behaviour of possibly very different
+programming languages, we do not want to impose one specific algebra
+for denoting actions, nor any specific communication mechanism. So we
+leave unspecified the constructors of the algebra that will allow building
+expressions and actions. Moreover, we use a generic {\em action interaction}
+mechanism, based on (some sort of) unification between two or more action
+expressions, to express various kinds of communication or
+synchronisation mechanisms.
+
+%\def\Talg{\mathcal{T}_{\Sigma,\P}}  % Moved to the header
+
+\noteSBin{proposed notations:
+
+  $g$ are boolean expressions;
+  $e_i$ are updates/assignments
+  \Ludo
+
+  In fact, I am not sure whether I have correctly understood this
+  suggestion: do you mean, \eg using $g$ to denote the set of
+  Boolean expressions or individual Boolean expressions? Using
+  lower case letters to denote sets might be problematic, since
+  we (at least I) use them a lot to denote instances, as in
+  \[q \goesto{a, g, e} q'\,.\]
+  In fact, I even use capital letters: in the definition of
+  interaction model composition, I use
+  \[\cdot \goesto{a, G, E} \cdot\]
+  in the conclusion of the rule.  However, for this latter I can
+  easily change the notation.
+
+  I have set up macros for, general and Boolean expressions,
+  actions, variables \etc[,] which I have substituted everywhere,
+  where appropriate in the following paragraph.
+}
+
+  \begin{tabular}{
+      @{}p{0.15\columnwidth}@{}
+      p{0.35\columnwidth}@{}
+      p{0.5\columnwidth}@{}
+    }
+    {\bf Output} & {\bf Command} & {\bf Definition}
+    \\
+    $\data$ &
+    {\ttfamily\textbackslash data} &
+    {\ttfamily\textbackslash sD}
+    \\
+    \signature &
+    {\ttfamily\textbackslash signature} &
+    {\ttfamily\textbackslash Sigma}
+    \\
+    \variables &
+    {\ttfamily\textbackslash variables} &
+    {\ttfamily\textbackslash cV}
+    \\
+    \Talg &
+    {\ttfamily\textbackslash Talg} &
+    {\ttfamily\textbackslash cT\_\{\textbackslash signature,\textbackslash variables\}}
+    \\
+    \actions{\#1} &
+    {\ttfamily\textbackslash actions\{\#1\}} &
+    {\ttfamily\textbackslash cA\_\{\#1\}}
+    \\
+    \guards{\#1} &
+    {\ttfamily\textbackslash guards\{\#1\}} &
+    {\ttfamily\textbackslash sB\^{}\{<\}\{\#1\}}
+    \\
+    \exprs{\#1} &       
+    {\ttfamily\textbackslash exprs\{\#1\}} &
+    {\ttfamily\textbackslash sE\_\{\#1\}}
+    \\
+    \assigns{\#1} &
+    {\ttfamily\textbackslash assigns\{\#1\}} &
+    {\ttfamily\textbackslash sA\_\{\#1\}}
+    \\
+    \valuations{\#1} &
+    {\ttfamily\textbackslash valuations\{\#1\}} &
+    {\ttfamily\textbackslash data\^{}\{\#1\}}
+    \\[6pt]
+    \val{\#2}{\#3} &
+    {\ttfamily\textbackslash val\{\#2\}\{\#3\}} &
+    {\ttfamily\#1\{\textbackslash sigma\}\^{}\{\#2\}\_\{\#3\}}
+    \\[6pt]
+    \val[\tilde]{\#2}{\#3} &
+    {\ttfamily\textbackslash val[\textbackslash tilde]\{\#2\}\{\#3\}} &
+    {\ttfamily\#1\{\textbackslash sigma\}\^{}\{\#2\}\_\{\#3\}}
+  \end{tabular}
+\noteSBin{commands above (tabular generates an error inside a
+  note)}
+
+Formally, we assume the existence of a term algebra $\Talg$,
+where $\signature$ is the signature of the data and action constructors,
+and $\variables$ a set of \emph{variables}. Within $\Talg$, we distinguish a set of
+\emph{data expressions} $\exprs{\variables}$ \replaceSB{, including}{and} a set of \emph{Boolean
+expressions} \todoLH{$\mathcal{B} \to g$}
+$\guards{\variables}$ ($\guards{\variables}\subseteq\exprs{\variables}$).
+On top of $\exprs{\variables}$ we build the \emph{action algebra}
+$\actions{\variables}$, with $\actions{\variables}\subseteq\Talg$ \replaceSB{,}{and}
+$\exprs{\variables}\cap\actions{\variables} = \emptyset$;
+naturally action terms will use data expressions as subterms.
+\addSB{In addition to the above notations, we will use
+\[
+\assigns{\variables} \bydef{=}
+\Setdef{(x_i := e_i)^{i \in I}}{
+  x_i^{i \in I}\subseteq \variables,
+  e_i^{i \in I}\subseteq \exprs{\variables},
+  I \text{ is a finite index set}
+}
+\]
+to denote the set of \emph{variable assignments}.}
+
+To be able to reason about the data flow between pLTSs, we
+distinguish \emph{input variables} of the form $?x$ within terms; the function
+$\vars(t)$ identifies the set of variables in a term
+$t\in\Talg$, and $iv(t)$ returns its input variables.
+Action algebras can \replaceSB{encode naturally }{naturally encode }usual point-to-point message passing calculi (using 
+$a(?x_1,\dots,?x_n)$ for inputs, $a(v_1,\dots,v_n)$ for outputs), but it also allows
+for more general mechanisms, like gate negotiation in Lotos, or broadcast
+communications.
+
+\addSB{%
+%
+  Finally, we assume the existence of a universal data domain
+  given as a partially-ordered set $(\data, \order)$, potentially
+  encompassing several copies of any given data type with
+  different orders.  For example, we assume that $(\data,
+  \order)$ comprises both the unordered set of Booleans $\sB =
+  (\{\true, \false\}, \emptyset)$ and the naturally ordered one
+  $\sB^< = (\{\true, \false\}, \{\false < \true\})$, and
+  similarly for integer and real numbers; as well as the set of
+  intervals ordered by inclusion.
+
+  For a set of variables $V \subseteq \variables$, we denote
+  $\valuations{V} \bydef{=} \{\val{}{}: V \rightarrow \data\}$
+  the set of \emph{valuations} of the variables in $V$.
+  Valuations extend canonically to expressions.  Thus
+  $\val{}{}(x)$ and $\val{}{}(e)$ denote, respectively, the
+  values of the variable $x$ and the expression $e$ under the
+  valuation $\val{}{}$.  For a valuation $\val{}{} \in
+  \valuations{V}$ and an assignment $(x_i := e_i)^{i \in I} \in
+  \assigns{V}$, we denote $\val{}{}[(x_i := e_i)^{i \in I}]$ the
+  valuation defined by
+  \[
+  \val{}{}\bigl[(x_i := e_i)^{i \in I}\bigr](x) \bydef{=}
+  \begin{cases}
+    \val{}{}(x), & \text{if } x \not\in x_i^{i \in I}\,,\\
+    \val{}{}(e_i), & \text{if } x = x_i, \text{for some } i \in I\,.
+  \end{cases}
+  \]
+  For two valuations $\val{1}{}, \val{2}{} : V \rightarrow
+  \data$, we denote \[\valdiff{\val{1}{}}{\val{2}{}} \bydef{=}
+  \setdefb{v \in V}{\val{1}{}(v) \neq \val{2}{}(v)}\] the set of
+  variables that are assigned different values by the two
+  valuations.  As usual, we write $\val{1}{} \order \val{2}{}$
+  iff $\val{1}{}(x) \order \val{2}{}(x)$, for all $x \in V$.  An
+  expression $e \in \exprs{V}$ is called \emph{monotonic} if, for
+  any two valuations $\val{1}{}, \val{2}{} \in \valuations{V}$,
+  $\val{1}{} \order \val{2}{}$ implies $\val{1}{}(e) \order
+  \val{2}{}(e)$.
+%
+}
+
+%****************************************************************
+%****************************************************************
+
+\section{The theory of architectures with data}
+\label{secn:archs}
+
+%****************************************************************
+
+\subsection{Components and composition}
+\label{sec:components}
 
@@
 }
-
-\subsection*{Unifying notations -- remarks}
-
-\todoLHin{proposed notations:}
-$g$ are boolean expressions
-$e_i$ are updates/assignments
-
-\todoLHin{Remove term algebra or simplify?}
-\todoLHin{universal domain $\implies$ remove sort}
-\todoLHin{replace assignments by $e_i$}
-
-\noteIn{In Archi we have $a$, whereas in pNets we have $\alpha$, where, approximately $\alpha = 
-a(x_1..x_n)$, except that $a$ is port name in archi and action name in pNets.
-Is this true? can we unify better? or is it sufficient?
-\Ludo
-
-$a$ is a set of ports, but otherwise, yes, this is true.  I think
-this is coherent, since, in archi, we have the ``interaction
-part'', \ie only ports, plus the data part, \ie variables,
-guards, expressions.  In pNets, these are combined.  So, it seems
-ok that notations differ\mdash ``uniformisation'' will be
-achieved by encoding archi $\rightarrow$ pNets.  \Simon }
-
-\noteIn{states looks ok, but initial state is $s_0$ in pNet and not in archi : $s^0$.  Exponent 
-position was removed from pNet because we found it complex with indexed set notation but 
-could be ok.
-\Ludo
-
-I am using exponent notation for ``modifiers'', reserving\mdash
-as much as possible\mdash index notation for enumeration.  I
-think this can be solved, where necessary, by using parentheses,
-\eg $(s^0_i)^{i \in I}$
-\Simon
-}
-
-%****************************************************************
-%****************************************************************
-
-\section{The theory of architectures with data}
-\label{secn:archs}
-
-%****************************************************************
-
-\subsection{Components and composition}
-\label{sec:components}
 
@@
     labelled by triples consisting of an \emph{interaction}
-    $\emptyset \neq a \subseteq P$, a Boolean \emph{guard} $g \in
-    \guards{V}$ and an \emph{update expression} $e \in
-    \exprs{V}$.
+    $\emptyset \neq a \subseteq P$, a monotonic Boolean \emph{guard} $g \in
+    \guards{V}$ and a monotonic \emph{update expression} \todoSB{$e \rightarrow u$}\hl{$e \in
+    \exprs{V}$}.
   \end{itemize}
@@
 always be clear from the context.
+
+%****************************************************************
+\subsection{Graphical representation of composed systems}
+\label{secn:connectors}
 
@@
 sub-trees.
-
-%\smallskip\noindent
-\paragraph*{Notations.}
-We extensively use indexed structures
-over some countable indexed sets, which are equivalent to mappings over
-the countable set. % . The indexes will usually be
-% integers, bounded or not. Such an indexed family is
-%denoted
-%follows:
-$a_i^{i\in I}$
-%, or equivalently  $(i\mapsto a_i)^{i\in I}$
-denotes a family of elements $a_i$ indexed over the
-set $I$. % Such a family
-% is equivalent to the mapping $(i\mapsto a_i)^{i\in I}$.
-% To specify the set over which the structure is indexed,
-% indexed structures are always denoted with an exponent of the form $i\in I$
-% (arithmetic only appears in the indexes if necessary).
-$a_i^{i\in I}$ defines both $I$ the set over which the family is
-indexed (called \emph{range}), and $a_i$ the elements of the family.
-E.g., $a^{i\in\{3\}}$ is the mapping with a single entry $a$ at index
-$3$ ; abbreviated $(3\mapsto a)$ in the following.
-When this is not
-ambiguous, we shall use notations for sets, and typically write
-``indexed set over I'' when formally we should speak of multisets, and
-write $x\in a_i^{i\in I}$ to mean $\exists i\in I.\, x=a_i$.  An empty
-family is denoted $\emptyset$. We
-denote classically with an overline -- $\overline{a}$  -- a family when the indexing set 
-is
-not meaningful.  $\uplus$ is the disjoint union on
-indexed sets.
-
-\paragraph*{Term algebra.}
-Our models rely on a notion of parameterised actions, that are
-symbolic expressions using data types and variables. As our model aims
-at encoding the low-level behaviour of possibly very different
-programming languages, we do not want to impose one specific algebra
-for denoting actions, nor any specific communication mechanism. So we
-leave unspecified the constructors of the algebra that will allow building
-expressions and actions. Moreover, we use a generic {\em action interaction}
-mechanism, based on (some sort of) unification between two or more action
-expressions, to express various kinds of communication or
-synchronisation mechanisms.
-
-\def\Talg{\mathcal{T}_{\Sigma,\P}}
-Formally, we assume the existence of a term algebra $\Talg$,
-where $\Sigma$ is the signature of the data and action constructors,
-and $\P$ a set of variables. Within $\Talg$, we distinguish a set of
-data expressions $\mathcal{E}_\P$, including a set of boolean
-expressions \todoLHin{$\mathcal{B} \to g$}
-$\mathcal{B}_{\P}$ ($\mathcal{B}_{\P}\subseteq\mathcal{E}_\P$).
-On top of $\mathcal{E}_\P$ we build the action algebra
-$\mathcal{A}_\P$, with $\mathcal{A}_P\subseteq\mathcal{T}_\P,
-\mathcal{E}_P\cap\mathcal{A}_P=\emptyset$;
-naturally action terms will use data expressions as subterms.
-To be able to reason about the data flow between pLTSs, we
-distinguish \emph{input variables} of the form $?x$ within terms; the function
-$\vars(t)$ identifies the set of variables in a term
-$t\in\AlgT$, and $iv(t)$ returns its input variables.
-Action algebras can encode naturally usual point-to-point message passing calculi (using 
-$a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs), but it also allows
-for more general mechanisms, like gate negociation in Lotos, or broadcast
-communications.
 

### 2018-02-14 2018-Arch-pNets/arch-pNets.tex
Some comments on the pNets section

@@
 \newcommand{\remove}[2][Removed]{\todo[color=red!20, size=\tiny]{#1}{\color{red}\st{#2}}}
+\newcommand{\removeIn}[2][Removed]{\todo[color=red!10, inline]{{\color{red}#2}#1}}
 %% \newcommand{\replace}[3][Replaced]{\todo[color=blue!20, size=\tiny]{#1}{\color{blue}#3}}
@@
 \newcommand{\removeSB}[1]{\remove[Removed by Simon]{#1}}
+\newcommand{\removeSBin}[1]{\removeIn[Removed by Simon]{#1}}
 \newcommand{\replaceSB}[2]{\replace[Replaced by Simon]{#1}{#2}}
@@
 
-A pLTS is a labelled transition system with variables; variables can be
-manipulated, defined, or accessed inside states, actions, guards, and
+A pLTS is a labelled transition system with variables\replaceSB{; variables}{. Variables} can be
+manipulated, defined, or accessed \noteSB{What does this mean?}\hl{inside states}, actions, guards, and
 assignments. Without loss of generality and to simplify the formalisation, we suppose 
@@
 %suppose that transitions looping to the same state does not do assignments.
-Note that we make no assumption on finiteness of the set of states nor
-on finite branching of the transition relation.
+Note that we make no assumption on \addSB{the }finiteness of the set of states, nor
+on \addSB{the }finite branching of the transition relation.
 
 We first define the set of actions a pLTS can use, let $a$
-range over action labels, $\symb{op}$ are operators, and $x_i$ range over
-variable names. Action terms are:\noteLH{Eric suggests to remove this: too precise. I 
-think last Expression should be removed not sure about the rest -- to be discussed}
-\[
+range over action labels\removeSB{, $\symb{op}$ are operators, and $x_i$ range over
+variable names}.
+Action terms are\replaceSB{:}{{} of the form $\alpha=a((?x_i)^{i \in I}, \symb{Expr}_j^{j \in J})$, where $(?x_i)^{i \in I}$ are input variables, $\symb{Expr}_j^{j \in J})$ are expressions.}\noteLH{Eric suggests to remove this: too precise.
+I
+think last Expression should be removed not sure about the rest -- to be discussed}\noteSB{I agree: expressions are not needed, but it is nice to explain how action terms are formed }
+\removeSBin{\[
 \begin{array}[l]{rcl@{\quad}p{5.5cm}}
@@
 \end{array}
-\]
-The input variables in an action term are those marked with a
-$\symb{?}$.
+\]}
+\removeSB{The input variables in an action term are those marked with a
+$\symb{?}$.}
 We additionally suppose that each input variable does not
-appear somewhere else in the same action term:
-$p_i=?x\Rightarrow\forall j\neq i.\, x\notin \vars(p_j)$
+appear \replaceSB{somewhere else }{anywhere }in the same action term\replace[Maybe? Not sure this is necessary.\Simon]{:
+$p_i=?x\Rightarrow\forall j\neq i.\, x\notin \vars(p_j)$}{.}
 
@@
 \item[$\bullet$]
-$S$ is a set of states.
+$S$ is a set of states\addSB{, $\vars(s)$ denotes the set of associated variables}.
 \item[$\bullet$]
-$s_0 \in S$ is the initial state.
+$s_0 \in S$ is the initial state.\noteSB{I usually put commas or semicolons in itemised lists}
 %\item[$\bullet$]
@@
 $L$ is the set of labels of the form
-
+% SB: I removed a new paragraph here, ok?
 $\langle \alpha,~g,~e\rangle$,
-where $\alpha \in\AlgA$ is a parameterised action, $g$ is a guard, and the variables 
+where \noteSB{I suggest using $\actions{V}$ (\ie \texttt{\textbackslash actions\{V\}}), with $V = \bigcup_{s \in S} \vars(s)$.}\hl{$\alpha \in\AlgA$} is a parameterised action, $g$ is a guard, and \hl{the variables
 $x_j\in \vars(s')$
 are assigned the updates in $e$.
+}\noteSB{I still have to update in my section, but it seems that my initial use of expressions conflicts with that in the SVs.
+I suggest writing explicitly $(?x_i := e_i)^{i \in I}$ or $\overline{?x := e}$ (not sure these should be input vars, though).}
 If 
@@
 \noteLH{is dom and codom clear?}
+\noteSB{Not sure: I understand, because I know what is meant, but this is not a canonical use, so should be explained.
+Will be solved if we roll back to \mbox{$(?x_i := e_i)^{i \in I}$} or \mbox{$\overline{?x := e}$}.}
 Now we define
@@
 A pNet has a set of sub-pNets that can be either pNets or pLTSs, and a
-set of Holes, playing the role of process parameters.
+set of \replaceSB{Holes}{holes}, playing the role of process parameters.
 
@@
 Actions involved at the pNet level (in the synchronisation vectors) do
-not need to distinguish  input 
-variables. Action terms for pNets are defined as follows:
+not \replaceSB{need to distinguish  input 
+variables. Action terms for pNets are defined as follows:}{have input variables, \ie they have the form $a(e_j^{j \in J})$.}
+\removeSBin{
 \[\begin{array}[l]{rcl@{\quad}l}
@@
 \]
+}
 
 \begin{definition}[pNets]\label{def-pnets}
-A pNet is a hierarchical structure where leaves are pLTSs and holes:\\
+A pNet is a hierarchical structure where leaves are pLTSs and holes:\\\noteSB{I would not put a new line here}
 $\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, J, \symb{SV}_k^{k\in 
@@
 \begin{itemize}
-\item[$\bullet$] $I \in \I$ is the set over which sub-pNets are indexed.
+\item[$\bullet$] \noteSB{This is clear from $\pNet_i^{i\in I}$.}\hl{$I \in \I$ is the set over which sub-pNets are indexed.}
 \item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets.
@@
 
-\item[$\bullet$] $J\!\in\!\I_\P$ is a set of indexes, called \emph{holes}.
+\item[$\bullet$] \noteSB{$I_P$ is not defined and, probably, not necessary.}\hl{$J\!\in\!\I_\P$} is a set of indexes, called \emph{holes}.
 $I$ and $J$ are \emph{disjoint}: $I\!\cap\! J=\emptyset$,  $I\!\cup\! J\neq\emptyset$
@@
 \item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
-  synchronisation vectors ($K\in\I_\P$). $\forall k\!\in\! K,
-  \symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k\,|\,g_k$ where
+  synchronisation vectors (\hl{$K\in\I_\P$}). $\forall k\!\in\! K,
+  \symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k\,|\,g_k$, where
   $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
@@
   J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
-$\Label(\symb{SV}_k) = \alpha'_k$. $g_k $ is a guard associated to the vector 
-$\vars(g_k)\subseteq \bigcup_{l\in I_k\uplus J_k}{\vars({\alpha_l})}$.
+\replaceSB{$\Label(\symb{SV}_k) = \alpha'_k$}{$\alpha'_k$, also denoted $\Label(\symb{SV}_k)$}. \replaceSB{$g_k $ is a guard associated to the vector 
+$\vars(g_k)\subseteq \bigcup_{l\in I_k\uplus J_k}{\vars({\alpha_l})}$.}{The Boolean expression $g_k $, such that $\vars(g_k)\subseteq \bigcup_{l\in I_k\uplus J_k}{\vars({\alpha_l})}$, is a guard associated to the vector.}
 
@@
   \begin{itemize}
-  \item The sort of a pNet is its signature, i.e. the set of actions it can
-perform. In the definition of sorts, we do not need to distinguish
-input variables (that specify the dataflow within LTSs), so for
+  \item  \noteSB{I think this can be lightened up a bit, since the definitions are all straightforward, whereas the notation is complex.
+Maybe reformulate in words and move the formal definitions in the appendix?}
+ The sort of a pNet is its signature, i.e. the set of actions it can
+perform.
+\noteSB{Is there any chance that, by writing assignments explicitly ($x := e$), we could eliminate the need to distinguish the input variables at all?
+That would simplify things.}\hl{In the definition of sorts, we do not need to distinguish
+input variables} (that specify the dataflow within LTSs), so for
 computing LTS sorts, we use a substitution operator\footnote{$\subst{y_k\gets x_k}^{k\in 
@@
 The semantics of open pNets will be defined  as an open automaton. An open
-automaton is an automaton where each transition composes transitions of several LTSs with
-action of some holes, the transition occurs if some predicates hold, and can involve a 
+automaton is an automaton where \noteSB{This might give a false impression that there is some kind of CCS-like ``duality'' between pLTSs and holes}\hl{each transition composes transitions of several LTSs with
+actions of some holes}, the transition occurs if some predicates hold, and can involve a 
 set of state modifications.
@@
 	\label{def:OpenTransitions}
-	An \emph{open transition} over a set  $(S_i,s_{0 i}, \rightarrow_i)^{i\in
-	I}$ of LTSs, a
+	An \emph{open transition} over a set \noteSB{In the architecture section, I say that we omit indices on $\goesto{}$ and that they are always clear from the context.}\hl{$(S_i,s_{0 i}, \rightarrow_i)^{i\in
+	I}$} of LTSs, a
 	set $J$ of holes with sorts $\Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is 
@@
         $i\in I$, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the
-	LTS $(S_i,s_{0 i}, \rightarrow_i)$, and $\xrightarrow{b_j}_j$
-        is a transition of the hole $j$, for any action $b_j$ in the
-        sort $\Sort_j$. $v$ is a variable denoting the resulting action
+	LTS $(S_i,s_{0 i}, \rightarrow_i)$, and \noteSB{Why insist on ``transition'' and $\goesto{b_j}_j$? Why not simply ``$b_j$ is an action in the sort $\Sort_j$?}\hl{$\xrightarrow{b_j}_j$
+        is a transition of the hole $j$}, for any action $b_j$ in the
+        sort $\Sort_j$.
+\noteSB{Why $v$?
+Why not $\alpha$?
+As now, it is not clear whether this is an action term or a variable $v \in \vars(s)$ of some hypothetical state $s$.}\hl{$v$ is a variable denoting the resulting action}
         of this open transition. \Pred\ is a predicate 
@@
     {A1_0 \OTarrow{\underline{\delta(x4)}} A1_1}
-  $
+  $\noteSB{The underline notation did not appear until here.}
 \end{example}
@@
 	An \emph{open automaton} is a structure\\ $A =
-	<\LTS_i^{i\in I},J,\mathcal{S},s_0,\mathcal{T}>$ where:
+	\langle\LTS_i^{i\in I},J,\mathcal{S},s_0,\mathcal{T}\rangle$, where:
 	\begin{itemize}
@@
 the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
-\[\Pred_{\symb{sv}}(SV, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow \bigg(
-\begin{array}{l}
+\begin{multline}
+  \Pred_{\symb{sv}}(SV, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow
+  \\
+%%   \bigg(
+%% \begin{array}{l}
 \exists {(a'_i)}^{i\in I},
-{(b'_j)}^{j\in J},v'.\, SV={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v' | g
-\\~~\land
+{(b'_j)}^{j\in J},v'.\, SV=\bigl({(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v' | g\bigr)
+\\
+\land
 \forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v' \land g
-\end{array} \bigg)\]
+%% \end{array} \bigg)
+\end{multline}
 \noteLH{Is and g sufficient? I would say yes}
+\noteSB{In principle, yes. I am not 100\% sure that the implicit dependency of $g$ on the variables in $a'_i$ and $b'_j$ is clear.}
 
@@
 	The semantics of a pNet $p$ is an open automaton $A = 
-	<Leaves(p),Holes(p),States(p),InitState(p),
-	\mathcal{T}>$ where $\mathcal{T}$ is the smallest set of open transitions		
+	\langle\symb{Leaves}(p),\symb{Holes}(p),\symb{States}(p),\symb{InitState}(p),
+	\mathcal{T}\rangle$, where \noteSB{We use $\cT$ for term algebra}\hl{$\mathcal{T}$} is the smallest set of open transitions		
 	satisfying the rules below:
@@
 	The second rule deals with pNet nodes: for each possible
-	synchronisation vector applicable to the rule subject, the premisses
+	synchronisation vector applicable to the rule subject, the premises
 	include one {\em open transition} for each sub-pNet involved, one possible
@@
 	expressed in terms of the leaves and holes of the pNet structure,
-	i.e. a flatten view of the pNet: e.g. $L$ is the index set of the
+	i.e. a \noteSB{Is this compatible with the ``compositionality'' argument?}\hl{flattened view of the pNet}: e.g. $L$ is the index set of the
 	Leaves, $L_m$ the index set of the leaves of one subnet indexed $m$, so all $L_m$
@@
 	\begin{description}
-		\item[{\bf Tr2:}]
+		\item[{\bf Tr2:}]\noteSB{I do not understand why the second line $pNet_m \models\dots$ is not subsumed by the first one?}
 	\end{description}

### 2018-02-16 2016-Weak-FH-Bisim/WeakBisim.tex
added guard in the proof
clean up macros and pushed semantics (improved) to the archi paper
Guards and leaves (reu)

@@
 
-\newcommand{\Pred}{\symb{Pred}}
-\newcommand{\Post}{\symb{Post}}
 %\usepackage[math]{cellspace}
@@
 % that we use for open-transitions
-
-\makeatletter
-\def \dotover {\textcolor{red}{\leavevmode\cleaders\hb@xt@ .22em{\hss $\cdot$\hss}\hfill\kern\z@}}
-\def \reddottedrule #1#2{\hbox {\advance \hsize by -0.5em
-%\sbox0{$\genfrac{}{}{0pt}{0}{#1}{#2}$} \phantom{\copy0} %
- {\ooalign{\vphantom{$\genfrac{}{}{0pt}{0}{#1}{#2}$}\cr\dotover\cr$\genfrac{}{}{0pt}{0}{#1}{#2}$\cr}}}}
-
- \def \dottedrule #1#2 {
-  {\sbox0{$\genfrac{}{}{0pt}{0}{#1}{#2}$}%
-    \vphantom{\copy0}%
-    \ooalign{%
-      \hidewidth
-      $\vcenter{\moveright\nulldelimiterspace
-        \hbox to\wd0{%
-         \xleaders\hbox{\kern.5pt\vrule height 0.4pt width 1.5pt\kern.5pt}\hfill
-          \kern-1.5pt
-        }%
-      }$
-      \hidewidth\cr
-    \box0\cr}}
-}
-
-\let \defaultfraction \mpr@@fraction
-\makeatother
 
@@
 %\newtheorem{proof}[theorem]{Proof}
-
-% Macros for the SOS rules and proof trees:
-%\newcommand\openrule[2]{\redinfer{#1}{#2}}
-\newcommand\openrule[2]{\inferrule*[myfraction=\reddottedrule,center]{#1}{#2}}
-%\newcommand\openrule[2]{\inferrule*{#1}{#2}}
-%\newcommand\ostate[1]{\triangleleft{\;#1\;}\triangleright}
-\newcommand\ostate[1]{\triangleleft{#1}\triangleright}
-\newcommand{\sm}[1]{\mbox{\boldmath\small #1}}
 
@@
 
+\TODO{state clearly that the next two definitions are mutually dependent}
+
 \begin{definition}[pNets]\label{def-pnets}
@@
   synchronisation vectors ($K\in\I_\P$). $\forall k\!\in\! K,
-  \symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k\,|\,g_k$ where
+  \symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k\,|\,e_k$ where
   $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
@@
   J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
-$\Label(\symb{SV}_k) = \alpha'_k$. $g_k \in \AlgB$ is a guard associated to the vector 
-$\vars(g_k)\subseteq \bigcup_{l\in I_k\uplus J_k}{\vars({\alpha_l})}$.
+$\alpha'_k$. $e_k \in \AlgB$ is a guard associated to the vector 
+$\vars(e_k)\subseteq \bigcup_{l\in I_k\uplus J_k}{\vars({\alpha_l})}$.
 
@@
 inductively as:
-\TODO{Nicer here at least}
 \[\begin{array}{l}
@@
 \overline{\Sort}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \biguplus_{i\in 
-I}\Leaves(\pNet_i)\uplus\{i\mapsto \pNet_i|\pNet_i=\pLTS\}}
+I}\Leaves(\pNet_i)\uplus\{i\mapsto \pNet_i|\pNet_i \text{ is a }\pLTS\}}
 \end{array}\]
@@
 \label{section:op-semantics}
-
-\TODO{update pred with guards}
 
@@
 \exists {(a'_i)}^{i\in I},
-{(b'_j)}^{j\in J},v'.\, SV={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v' | g
+{(b'_j)}^{j\in J},v'.\, SV={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v' | e_b
 \\~~\land
-\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v' \land g
+\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v' \land e_b
 \end{array} \bigg)\]
@@
     {k\!\in\! K \\SV_k \!=\! \alpha_m^{m \in I\uplus J} \!\to\! 
-    \alpha' |g \\
+    \alpha' |e_b \\
     	Leaves(\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in 
@@
 v=\alpha'
-$. Modulo renaming of fresh variables, this is identical to the predicate that occurs in 
+\land g$. Modulo renaming of fresh variables, this is identical to the predicate that 
+occurs in 
 the source open transition except $\alpha_{j_0}=v_{j_0}$ has been replaced by  
@@
 $P[Q]_{j_0}$, assembling their predicates.
-
+\TODO{LUDO: REPROVE}
 \begin{lemma}[Open transition composition]\label{lem-compose} 

### 2018-02-16 2016-Weak-FH-Bisim/WeakBisim.tex

@@
 $P[Q]_{j_0}$, assembling their predicates.
-\TODO{LUDO: REPROVE}
+
 \begin{lemma}[Open transition composition]\label{lem-compose} 
@@
 
-       Consider each premise of the open transition (constructed by TR2 in 
+       Consider each premise of the open transition (constructed by Tr2 in 
 Definition~\ref{def:operationalSemantics}). 
@@
 $K$ and the synchronisation vector are unchanged ($j_0$ is now in the set of sub-pNets); 
-$SV=clone(\alpha_j^{j\in I_k\uplus\{j_0\}\uplus 
-	J_k})$. $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$. All sub-pNets can be 
+$SV_k=\alpha_j^{j\in I\uplus\{j_0\}\uplus 
+	J} \!\to\! 
+    \alpha' |e_b$. $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$. $I$ and $J$ are the 
+    set of leaves and holes of $P$, $I'$ and $J'$ are the sets of moving leaves and holes 
+    in the reduction of $P$. All sub-pNets of 
+    must
+    be 
 reduced:\\[-2ex]%\footnote{again we skip arguments related to renaming of fresh 
 %variables}:
-\[\forall m\in I_k\cup \{j_0\}.
-\pNet_m \models
+\[\forall m\!\!\in\!\! I\cup \{j_0\}. 	
+    {\left(\begin{array}{l}
+	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
+    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
+    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
+    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
+    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
+		{ \pNet_m 
+    	 \models
     	\inferrule*[myfraction=\reddottedrule]
-{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I'_m},
-	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
-{\ostate{s_{i}^{i \in L_k}} \OTarrow {v_m}
-	\ostate{s_{i}'^{\, i \in L_k}}}\]
-the last sub-pNet is the one filled by $Q$ which offers an open transition by hypothesis.
-Let $I'=\biguplus_{m\in I_k} I_m \uplus I_Q = I \uplus I_Q$ and $J'= \biguplus_{m\in I_k} 
-J_m \uplus J_Q \uplus J_k = J\setminus\{j_0\}\uplus J_Q$. The predicate for the open 
-transition is: $\Pred\,''=\bigwedge_{m\in I_k}\Pred_m \land \Pred\,'
-\land \Pred(SV,a_i^{i\in I_k}\uplus(j_0\mapsto v_Q),b_j^{j\in J_k},v)$. By definition 
-$\Pred(SV,a_i^{i\in I_k}\uplus(j_0\mapsto v_Q),b_j^{j\in J_k},v)\Leftrightarrow
-	\forall i\in I_k.\, a_i=\alpha_i\land \forall j \in J_k.\, b_j=\alpha_j \land 
-	\alpha'_k=v\land v_Q=\alpha_{j_0}$, finally $\Pred\,''=\Pred\subst{b_{j_0}\leftarrow 
+    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
+    	{\ostate{s_m} \OTarrow {v_m}
+    		\ostate{s_m'}} \land I'_m=\{m\} \land J'_m=\emptyset}
+\end{array}\right)}\]
+the sub-pNet at position $j_0$ is the one filled by $Q$ which offers an open transition 
+by hypothesis.
+Let $I''=\biguplus_{m\in I} I'_m \uplus I_Q = I' \uplus I_Q$ and $J''= \biguplus_{m\in I} 
+J_m \uplus J_Q \uplus J = J'\setminus\{j_0\}\uplus J_Q$. The predicate for the open 
+transition is: $\Pred\,''=\bigwedge_{m\in I}\Pred_m \land \Pred\,'
+\land \Pred(SV_k,a_i^{i\in I_k}\uplus(j_0\mapsto v_Q),b_j^{j\in J},v)$. By definition 
+$\Pred(SV_k,a_i^{i\in I}\uplus(j_0\mapsto v_Q),b_j^{j\in J},v)\Leftrightarrow
+	\forall i\in I.\, a_i=\alpha_i\land \forall j \in J.\, b_j=\alpha_j \land 
+	\alpha'_k=v\land v_Q=\alpha_{j_0}\land e_b$, finally 
+	$\Pred\,''=\Pred\subst{b_{j_0}\leftarrow 
 	v_Q} \land \Pred\,'$. The post-condition gathers the post-conditions related to all 

### 2018-03-01 2016-Weak-FH-Bisim/WeakBisim.tex
Changements durant skype simon
Update dessin de Bisim

@@
     \alpha' |e_b \\
-    	Leaves(\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in 
+    	Leaves(\mylangle \pNet_i^{i\in I'}, \overline{\Sort}, \symb{SV}_k^{k\in 
     	K}\myrangle) \!=\! \pLTS_l^{l\in L} \\    	
@@
     }
-    {\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
+    {\mylangle \pNet_i^{i\in I'}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
     	\models
@@
 	\includegraphics[width=\linewidth]{XFIG/Bisim}
-	\TODO{J'ai remis $\mathcal{R}$, mais c'est un abus de notation, le $\Pred_{s,t}$ n'apparait pas dans la figure...}
+	\TODO{J'ai ajoute les predicats. Il reste a dessiner la ``couverture'' si j'y arrive...}
 \end{minipage}
@@
 \end{mathpar}
- such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in 
+ such that  $\forall x, J_1=J_{x}, \exists \Pred_{s',t_x}. (s',t_x|\Pred_{s',t_x})\in 
  \mathcal{R}$; 
@@
 
+     \TODO{Eric: j'ai ajoute $\exists$ sur les predicats $\Pred_{s',t_x}$, qui n'etaient pas definis...}
+
  \item  and symmetrically any open transition from $t$ in $\mathcal{T}_2$ can be 
@@
 the predicate associated to the relation between the initial states is true.
-\TODO{do we want formulas for this?}
+% \TODO{do we want formulas for this?}
  \end{definition}
@@
 \medskip
-\ERIC{If we assume that everything is finite (states and transitions in the
+If we assume that everything is finite (states and transitions in the
 open automata, and the predicates in $\mathcal{R}$, then it is easy to
@@
 FH-bisimulation, provided the logic of the predicates is decidable (see
-\cite{henrio:Forte2016}). }
+\cite{henrio:Forte2016}).
 

### 2018-03-07 2018-Arch-pNets/arch-pNets.tex
Guards and leaves (reu)
Changements durant skype simon
Before skype: shorter def 11 and cleaned up a bit expression (now tex compiles)

@@
 range over action labels\removeSB{, $\symb{op}$ are operators, and $x_i$ range over
-variable names}.
-Action terms are\replaceSB{:}{{} of the form $\alpha=a((?x_i)^{i \in I}, \symb{Expr}_j^{j \in J})$, where $(?x_i)^{i \in I}$ are input variables, $\symb{Expr}_j^{j \in J})$ are expressions.}\noteLH{Eric suggests to remove this: too precise.
-I
+variable names}. Action terms are\replaceSB{:}{{} of the form $\alpha=a((?x_i)^{i \in I}, 
+\Expr_j^{j \in J})$, where $(?x_i)^{i \in I}$ are input variables, $\Expr_j^{j \in J})$ 
+are expressions.}\noteLH{Eric suggests to remove this: too precise. I 
 think last Expression should be removed not sure about the rest -- to be discussed}\noteSB{I agree: expressions are not needed, but it is nice to explain how action terms are formed }
-\removeSBin{\[
-\begin{array}[l]{rcl@{\quad}p{5.5cm}}
-  \alpha\in\AlgA&::=&a(p_1,\ldots,p_n)&\text{action terms}\\
-  p_i&::=& ?x~|~\symb{Expr}&\text{parameters (input variable or expression)}\\
-  \symb{Expr}&::=& 
-  \symb{Value}~|~x~|~\symb{op}(\symb{Expr}_1,..,\symb{Expr}_n)&\text{Expressions}
-\end{array}
-\]}
+\removeSBin{def of $\AlgA$, $p_i$, $\Expr$}
+%\[
+%\begin{array}[l]{rcl@{\quad}p{5.5cm}}
+%  \alpha\in\AlgA&::=&a(p_1,\ldots,p_n)&\text{action terms}\\
+%  p_i&::=& ?x~|~\Expr&\text{parameters (input variable or expression)}\\
+%  \Expr&::=& 
+%  \symb{Value}~|~x~|~\symb{op}(\Expr_1,..,\Expr_n)&\text{Expressions}
+%\end{array}
+%\]
 \removeSB{The input variables in an action term are those marked with a
@@
 not \replaceSB{need to distinguish  input 
-variables. Action terms for pNets are defined as follows:}{have input variables, \ie they have the form $a(e_j^{j \in J})$.}
+variables. Action terms for pNets are defined as follows:}{have input variables, \ie they 
+have the form $a(\Expr_j^{j \in J})$.}
 \removeSBin{
-\[\begin{array}[l]{rcl@{\quad}l}
-  \alpha\in \AlgAS &::=&a(Expr_1,\ldots,Expr_n)
-\end{array}
-\]
+%\[
+%\begin{array}[l]{rcl@{\quad}l}
+$  \alpha\in \AlgAS ::=a(\Expr_1,\ldots,\Expr_n)$
+%\end{array}
+%\]
 }
@@
 \overline{\Sort}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \biguplus_{i\in 
-I}\Leaves(\pNet_i)\uplus\{i\mapsto \pNet_i|\pNet_i=\pLTS\}}
+I}\Leaves(\pNet_i)\uplus\{i\mapsto \pNet_i|\pNet_i\pNet_i \text{ is a }\pLTS\}}
 \end{array}\]
@@
 
-A pNet $Q$ is \emph{closed} if it has no hole: $\Holes(Q)=\emptyset$; else it
+\noteLHin{Below a simpler def 11}
+\begin{definition}[Sorts, Holes, Leaves of pNets]
+  \begin{itemize}
+  \item 
+ The sort of a pNet is its signature, i.e. the set of actions it can
+perform. A sort is a set of action signature, where each action signature is an action 
+label plus the arity of the action.
+
+\item
+The set of holes $\Holes(\pNet_{i_1})$ of a pNet is the indexes of the holes of the pNet 
+itself plus the indexes of all the holes of its subnets (we suppose those indexes 
+disjoints).
+%
+%defined inductively; the sets of holes
+%in a pNet node and its subnets are all disjoint:
+%  \[\begin{array}{l}
+%\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset \\
+%\Holes(\mylangle \pNet_i^{i\in I}\!,\Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) 
+%=J\uplus{\displaystyle \bigcup_{i\in 
+%I}\Holes(\pNet_i)}\\
+%\forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
+%\forall i_1,i_2\in I.\,i_1\neq i_2\Rightarrow  
+%\Holes(\pNet_{i_1})\cap\Holes(\pNet_{i_2})=\emptyset
+%\end{array}\]
+\item
+The set of leaves of a pNet is the set of all pLTSs occurring in the structure, as an 
+indexed family of the form $\Leaves(\pNet)= \mylangle \pNet_i \myrangle^{i \in L}$.
 is said to be \emph{open}.
@@
 	hold \emph{after the open transition}, they are represented as a substitution of the 
-	form $\{x_k\gets e_k\}^{k\in K}$ 
+	form $\{x_k\gets \Expr_k\}^{k\in K}$ \noteLH{considering the level of abstraction I 
+	would like to just put $\Post_=e$}
 	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
@@
 \begin{multline}
-  \Pred_{\symb{sv}}(SV, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow
+  \Pred_{\symb{sv}}(SV, 
+  a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow
   \\
+%\exists 
 %%   \bigg(
 %% \begin{array}{l}
-\exists {(a'_i)}^{i\in I},
-{(b'_j)}^{j\in J},v'.\, SV=\bigl({(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v' | g\bigr)
+\exists {\vars((a'_i)}^{i\in I}),
+{\vars((b'_j)}^{j\in J}),\vars(v').\, %SV=
+%\\
+%\land
+\\\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v' \land g
+%% \end{array} \bigg)
 \\
-\land
-\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v' \land g
-%% \end{array} \bigg)
+\text{ Where } SV=\bigl({(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v' | g\bigr)
 \end{multline}
@@
     \alpha' |g \\
-    	Leaves(\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in 
+    	Leaves(\mylangle \pNet_i^{i\in I'}, \overline{\Sort}, \symb{SV}_k^{k\in 
     	K}\myrangle) \!=\! \pLTS_l^{l\in L} \\    	

### 2018-03-08 2016-Weak-FH-Bisim/WeakBisim.tex
WEAK: removed a TODO and added a TODO section at the begining

--- 2018-03-01 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
-\TODO{state clearly that the next two definitions are mutually dependent}
+We now define the structure of pNets, the following definition relies on the definition 
+of holes, leaves and sorts provided below in Definition~\ref{def-sortholeleave}.
 
@@
 
-The preceding definition relies on the auxiliary functions below:
-
-\begin{definition}[Sorts, Holes, Leaves of pNets]
+The preceding definition relies on the auxiliary functions defined below:
+
+\begin{definition}[Sorts, Holes, Leaves of pNets]\label{def-sortholeleave}
   \begin{itemize}
@@
 \end{array} \bigg)\]
-\LUDO{Is and g sufficient? I would say yes}
 

### 2018-03-14 2016-Weak-FH-Bisim/WeakBisim.tex
TODO section
improved text of todo
new SV syntax

--- 2018-03-08 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 \end{abstract}
+
+\section{Status and TODO list}
+Improve and simplify Tr2
+
+notation guards in  SV
 
@@
   synchronisation vectors ($K\in\I_\P$). $\forall k\!\in\! K,
-  \symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k\,|\,e_k$ where
+  \symb{SV}_k\!=\!\SV{\alpha_{l}^{l\in I_k \uplus J_k}}{\alpha'_k}{e_k}$ where
   $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
@@
 \exists {(a'_i)}^{i\in I},
-{(b'_j)}^{j\in J},v'.\, SV={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v' | e_b
+{(b'_j)}^{j\in J},v'.\, SV=\SV{{(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}} {v'} {e_b}
 \\~~\land
@@
     $\inferrule
-    {k\!\in\! K \\SV_k \!=\! \alpha_m^{m \in I\uplus J} \!\to\! 
-    \alpha' |e_b \\
+    {k\!\in\! K \\SV_k \!=\! \SV{\alpha_m^{m \in I\uplus J}}{\alpha'}{e_b} \\
     	Leaves(\mylangle \pNet_i^{i\in I'}, \overline{\Sort}, \symb{SV}_k^{k\in 
@@
 $K$ and the synchronisation vector are unchanged ($j_0$ is now in the set of sub-pNets); 
-$SV_k=\alpha_j^{j\in I\uplus\{j_0\}\uplus 
-	J} \!\to\! 
-    \alpha' |e_b$. $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$. $I$ and $J$ are the 
+$SV_k=\SV{\alpha_j^{j\in I\uplus\{j_0\}\uplus 
+	J}}{\alpha'}{e_b}$. $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$. $I$ and $J$ 
+	are the 
     set of leaves and holes of $P$, $I'$ and $J'$ are the sets of moving leaves and holes 

### 2018-03-20 2016-Weak-FH-Bisim/WeakBisim.tex
weakbisim running example

--- 2018-03-14 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
-notation guards in  SV
+X notation guards in  SV
 
@@
  \includegraphics[width=4.5cm]{XFIG/TransportSpec}
-  \caption{Schema and specification of the protocol }  \label{schema:enable-pnets}
+  \caption{Schema and specification of the protocol }  \label{schema:ABP-pnets}
 %\end{minipage}
@@
 %\begin{minipage}{6cm}
-  \centerline{\includegraphics[width=11cm]{XFIG/ABPSchema}}
-  \caption{Composed pNet with the ABP protocol}  \label{schema:enable-composed}
+  \centerline{\includegraphics[width=11cm]{XFIG/ABP3-Schema}}
+  \caption{Composed pNet with the ABP protocol}  \label{schema:ABP-composed}
 %\end{minipage}
@@
 \begin{example}\emph{An open-transition.}
-  \label{OT:enable-composed}
-  The \texttt{EnableCompL} pNet of Fig. \ref{schema:enable-composed} has 2 controllers and 2 holes. One of its possible open-transition is:
+  \label{OT:ABP}
+  The \texttt{ABP} pNet of Fig. \ref{schema:ABP-composed} has 2 controllers and 2 holes. One of its possible open-transition is:
 
@@
  $  OT_2  = \openrule{
-                       0 \xrightarrow{\delta}_{C_3} 1 ~~
-                            0 \xrightarrow{l}_{C_4} 0  ~~                 
-                            \xrightarrow{\delta(x4)}_P ~~
-                            \xrightarrow{accept(x4)}_Q 
+                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
+                            \xrightarrow{in(?m,?b)}_{M1}
                       }
   %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
-    {A1_0 \OTarrow{\underline{\delta(x4)}} A1_1}
+    { \OTarrow{\ostate{1,0,0,0}\underline{send(m,b)}} \ostate{2,1,0,0}}
   $
@@
 	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
-    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
-    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
+    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m},
+    	\{\xrightarrow{b_{j}}_j\}^{j\in J_m}, \Pred_m, \Post_m}
     	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
@@
     	{\ostate{s_m} \OTarrow {v_m}
-    		\ostate{s_m'}} \land I'_m=\{m\} \land J'_m=\emptyset}
+    		\ostate{s_m'}} \land I_m=\{m\} \land J_m=\emptyset}
 \end{array}\right)}\\
@@
     	%Leaves(\pNet_m) = \overline{\pLTS}^{L_k})  	
-     J' = \biguplus_{m\in I}\!\! J'_m \uplus J 	\\
+     J' = \biguplus_{m\in I}\!\! J_m \uplus J 	\\
     	\Pred = \bigwedge_{m\in I}\!\! \Pred_m \land
     	\Pred_{\symb{sv}}(SV_k,v_m^{m\in I},b_j^{j\in J},v)\\ 
-    		I' = \biguplus_{m\in I}\!\! I_m'
+    		I' = \biguplus_{m\in I}\!\! I_m
     	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
@@
   In Fig. \ref{usingrules:OT2} we show the deduction tree used to construct and prove the 
-  open transition $OT_2$ of \texttt{EnableCompL} (see example page \pageref{OT:enable-composed}).
+  open transition $OT_2$ of \texttt{EnableCompL} (see example page \pageref{OT:ABP-composed}).
   The rule uses TR1 for the $\delta$ transition of $C_3$, for the $l$ transition of $C_4$, then combines the result using the $a_4$ vector of the bottom pNet node, and the $\underline{\delta(x)}$ vector of the top node.
@@
 
-2b) For each of the obtained deduction trees, extract the resulting
-open-transition, with its predicate and \Post\ assignments by exploring the structure of 
-the pNet.
-
-2c)
-\ERIC{The predicate is submitted to Z3 for checking satisfiability. If it is NOT stisfiable, the resulting OT is discarded. This will minimize the number of
-resulting transitions, and potentialy prune the search-space.}
-
-2d)
+2b) For each of the obtained deduction trees:\\
+- Extract the resulting open-transition, with its predicate and
+\Post\ assignments by exploring the structure of the pNet.
+
+- The predicate is submitted to Z3 for checking satisfiability. If it
+is NOT stisfiable, the resulting OT is discarded. This will minimize
+the number of resulting transitions, and potentialy prune the search-space.
+
+- For each open-transition,  add the transition in the outgoing transitions of
+the current state, and add the
+resulting state in the unexplored set if it is not already there.
+
+%3) this ends with the "while" from step 2, when we have no more
+%unexplored set.
+\end{algorithm}
+
+Given an open-pNet
+with finite synchronisation sets, finitely many leaves and
+holes, and each pLTS at leaves having a finite number of states and
+(symbolic) transitions, has a finite automaton (see \ref{Forte}).
+
+\subsection{Post-processing: Elimination of intermediate variables}
+
 \ERIC{Optionally, simplify the predicate by eliminating the unnecessary intermediate variables, that were produced as fresh local variables of synchronisation vectors, and fresh result variables of intermediate OTs.
@@
 - the result action at toplevel.}
-
-For each open-transition,  add the transition in the outgoing transitions of
-the current state, and add the
-resulting state in the unexplored set if it is not already in the
-explored set.
-
-%3) this ends with the "while" from step 2, when we have no more
-%unexplored set.
-\end{algorithm}
-
-Given an open-pNet
-with finite synchronisation sets, finitely many leaves and
-holes, and each pLTS at leaves having a finite number of states and
-(symbolic) transitions, has a finite automaton (see \ref{Forte}).
 
@@
 	\includegraphics[width=\linewidth]{XFIG/Bisim}
-	\TODO{J'ai ajoute les predicats. Il reste a dessiner la ``couverture'' si j'y arrive...}
+%	\TODO{J'ai ajoute les predicats. Il reste a dessiner la ``couverture'' si j'y arrive...}
 \end{minipage}
@@
 
-     \TODO{Eric: j'ai ajoute $\exists$ sur les predicats $\Pred_{s',t_x}$, qui n'etaient pas definis...}
+%     \TODO{Eric: j'ai ajoute $\exists$ sur les predicats $\Pred_{s',t_x}$, qui n'etaient pas definis...}
+
+ \item  and symmetrically any open transition from $t$ in $\mathcal{T}_2$ can be 
+      covered by a set of transitions from $s$ in $\mathcal{T}_1$.
+ \end{itemize}
+
+% \TODO{Eric: il reste des petits bugs genre $s^{2'}_x$ plutot que
+%   $s^{2}_x$}
+
+%Where $\symb{Subst}(\Pred,\Post)$ is the parallel substitution of all
+%assigned variables.
+Two pNets are FH-bisimilar if there exist a relation between their associated 
+automata that is an FH-bisimulation and their initial states are in the relation, i.e. 
+the predicate associated to the relation between the initial states is true.
+% \TODO{do we want formulas for this?}
+ \end{definition}
+Classically, $\Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}$
+applies in parallel the  
+substitutions $\Post_{OT}$ and $\Post_{OT_x}$ (parallelism is crucial
+inside each $\Post$ set but $\Post_{OT}$ is independent from
+$\Post_{OT_x}$), applying the assignments of the involved rules.
+
+\medskip
+If we assume that everything is finite (states and transitions in the
+open automata, and the predicates in $\mathcal{R}$, then it is easy to
+prove that it is decidable whether a relation is a 
+FH-bisimulation, provided the logic of the predicates is decidable (see
+\cite{henrio:Forte2016}).
+
+\subsection{Post-processing: Elimination of intermediate variables}
+
+\ERIC{Optionally, simplify the predicate by eliminating the unnecessary intermediate variables, that were produced as fresh local variables of synchronisation vectors, and fresh result variables of intermediate OTs.
+In the resulting predicate the only significant variables are :\\
+- the input variables of pLTS transitions\\
+- the actions of holes\\
+- the result action at toplevel.}
+
+  \TODO{Eric: define ``elimination of intermediate variables ?'' it
+    transforms the predicates, it is not an
+    ``equivalence'' transformation, rather some sort of
+    abstraction... Does it change the satisfiability ?}
+
+\subsection{Running example}
+
+\TODO{Eric: full result of the tool execution on the running
+  example. Full ? certainly not, just a subset...}
+
+\section{Bisimulation}
+\label{section:bisimulation}
+
+	Now we use our symbolic operational semantics to define a notion of
+	strong (symbolic) bisimulation. Moreover this equivalence is decidable whenever we 
+	have some
+	decision procedure on the predicates of the action algebra.
+
+%% , that we prove compatible with the
+%% composition of open pNets. \TODO{do we really know this ?}
+
+The equivalence we need is a strong bisimulation between
+pNets having exactly the same Holes with the same sorts, but using a
+flexible matching 
+between open transition, to accommodate comparisons between pNet
+expressions with different architectures.
+ We name it FH-bisimulation,
+ as a short cut for the ``Formal Hypotheses'' manipulated in the
+ transitions, but also as a reference to the work of De Simone~\cite{deSimone85},
+ that pioneered this idea.
+
+Let $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$ be a relation over the set $\mathcal{S}_1$ and 
+$\mathcal{S}_2$ constrained by a predicate.
+More precisely, for any pair $(s,t)$, there is a 
+   single
+      $(s,t|\Pred_{s,t})\in\mathcal{R}$  stating that $s$ and $t$ are related 
+      if $\Pred_{s,t}$ 
+      is 
+      true, i.e. the states are related when the variables in $s$ and $t$ verify the 
+      predicate $\Pred_{s,t}$.
+ FH-bisimulation is defined formally: 
+ \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim}
+
+\noindent
+\begin{minipage}{0.69\linewidth} 	Suppose that
+   $A_1 = <\overline{\LTS_1},J,\mathcal{S}_1, s_0,
+   \mathcal{T}_1>$ and $A_2 = <\overline{\LTS_2},J,\mathcal{S}_2,t_0, \mathcal{T}_2>$
+   are open automata where the set
+   of holes are equal 
+   and of the same sort.
+
+ Then 
+$\mathcal{R}$ is an FH-bisimulation iff for any  states
+$s\in\mathcal{S}_1$ and $t\in\mathcal{S}_2$, $(s,t|\Pred_{s,t})\in\mathcal{R}$, we 
+have
+the following:
+\end{minipage}
+\hspace{2mm}
+\begin{minipage}{0.30\linewidth}
+	\includegraphics[width=\linewidth]{XFIG/Bisim}
+%	\TODO{J'ai ajoute les predicats. Il reste a dessiner la ``couverture'' si j'y arrive...}
+\end{minipage}
+
+ \begin{itemize}
+ \item  For any open transition $OT$ in $\mathcal{T}_1$:
+ \begin{mathpar}
+     \inferrule*[myfraction=\reddottedrule]
+         {\{s_i\xrightarrow{a_i}_i s'_i\}^{i\in I_1}, % , s_i,s'_i\in 
+         %States(I_1)
+           \{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
+         {s \OTarrow {v} s'}
+
+\end{mathpar}
+ there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
+ \begin{mathpar}
+%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
+    \inferrule*[myfraction=\reddottedrule]
+         {\{t_i\xrightarrow{a_{i x}}_i t_{i x}\}^{i\in I_{ x}},
+           \{\xrightarrow{b_{j x}}_j\}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {t \OTarrow {v_x} t_x}
+%         \right)
+\end{mathpar}
+ such that  $\forall x, J_1=J_{x}, \exists \Pred_{s',t_x}. (s',t_x|\Pred_{s',t_x})\in 
+ \mathcal{R}$; 
+ and  \\
+ $\Pred_{s,t} \land \Pred_{OT}\\
+\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
+   \left( \forall j. b_j=b_{jx}  \Rightarrow \Pred_{OT_x}
+     \land v\!=\!v_x \land  
+     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
+     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
+     %     \right)$.
+
+%     \TODO{Eric: j'ai ajoute $\exists$ sur les predicats $\Pred_{s',t_x}$, qui n'etaient pas definis...}
 
@@
 
+\def\InvAct{\mathcal{Inv}}
+
 \begin{definition}[Weak open transitions]
@@
   We define $\mathcal{T^*}$ the \emph{weak open transition relation}
-  with respect to a set of invisible actions $\mathcal{I}$ as:
+  with respect to a set of invisible actions $\InvAct$ as:
 
@@
 \end{definition}
+
+\subsection{Running example}
+- Detail of a $\tau$* sequence, \\
+- construction of the predicate\\
+- defn / elimination of the intermediaite variables\\
+- construction of the weak OT.
+
+\noindent
+$\ostate{1000}\OTarrow{m\_rec(m,x), \phi_1 = [x=s_1\_b \land
+    m=s_1\_m]}\ostate{2100}$\\
+$\qquad\ostate{2100}$ variables: $\psi_1 = \{m_1\_m:=m; m_1\_x:=x; s_2\_b:=s_1\_b\}$;\\
+\\
+$\ostate{2100}\OTarrow{\tau <m\_send(m_1\_m,m_1\_x), r\_rec(?m',?b)>,
+  \phi_2 = [r_0\_b=b \land m'=m_1\_m \land b=m_1\_x]}\ostate{2001}$\\
+$\qquad\ostate{2001}$ variables: $\psi_2 = \{r_1\_b:=r_0\_b; r_1\_m:=m;
+...\}$;\\
+\\
+$\ostate{2001}\OTarrow{v,
+  \phi_3 = [v=out(r_1\_m)]}\ostate{2002}$\\
+$\qquad\ostate{2002}$ variables: $\psi_3 = \{r_2\_b:=r_1\_b\}$;\\
+
+Resulting Weak Transition:
+
+\noindent
+$\ostate{1000}\OTWeakarrow{v,
+  \phi = \phi_1\land\phi_2\psi_1\land\phi_3\psi_2\psi_1}\ostate{2002}$\\
+\\
+$\phi=[x=s_1\_b \land m=s_1\_m\\
+  \land r_0\_b=b \land m'=m_1\_m \land b=m_1\_x\\
+  \land v=out(r_1\_m)]\\
+and \\
+\psi= \{r_2\_b:=r_0\_b\}$
+
+Note that in $\phi$ the application of assignments
+$\psi_1,\psi_2,\psi_3$ have already ``eliminated'' the intermediate
+state variables
+$m_1\_m, b=m_1\_x, r_1\_m$, but not the intermediate input variables
+$m,m',x,b$. But now $\phi$ includes enough information to eliminate them, giving
+a final $\phi'= [v=out(s_1\_m)\land r_0\_b=s_1\_b]$
 
@@
 Using the usual encoding of the Lotos Enable operator (see
-Fig. \ref{schema:enable-pnets}), we build now open automata for two  
+Fig. \ref{schema:ABP-pnets}), we build now open automata for two  
 open pNets \texttt{P>>(Q>>R)} and \texttt{(P>>Q)>>R)}, and 
@@
 \pNet_m \models\inferrule*[myfraction=\reddottedrule]
-    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
-    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
+    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m},
+    	\{\xrightarrow{b_{j}}_j\}^{j\in J_m}, \Pred_m, \Post_m}
     	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
@@
     	{\ostate{s_m} \OTarrow {v_m}
-    		\ostate{s_m'}} \land I'_m=\{m\} \land J'_m=\emptyset}\]
+    		\ostate{s_m'}} \land I_m=\{m\} \land J_m=\emptyset}\]
 
@@
 the OT of $P$ let $I'= 
-\biguplus I'_m=I\setminus L_Q$, $J'=\biguplus J'_m\uplus J
+\biguplus I_m=I\setminus L_Q$, $J'=\biguplus J_m\uplus J
 \uplus\{j_0\}=J\setminus\Holes(Q)\uplus \{j_0\}$;  the predicate is 
@@
     	{\ostate{s_m} \OTarrow {v_m}
-    		\ostate{s_m'}} \land I'_m=\{m\} \land J'_m=\emptyset}
+    		\ostate{s_m'}} \land I_m=\{m\} \land J_m=\emptyset}
 \end{array}\right)}\]
@@
 by hypothesis.
-Let $I''=\biguplus_{m\in I} I'_m \uplus I_Q = I' \uplus I_Q$ and $J''= \biguplus_{m\in I} 
+Let $I''=\biguplus_{m\in I} I_m \uplus I_Q = I' \uplus I_Q$ and $J''= \biguplus_{m\in I} 
 J_m \uplus J_Q \uplus J = J'\setminus\{j_0\}\uplus J_Q$. The predicate for the open 

### 2018-03-20 2016-Weak-FH-Bisim/WeakBisim.tex
smalltypo

@@
 \subsection{Running example}
-- Detail of a $\tau$* sequence, \\
+- Detail of a $\tau^*$ sequence, \\
 - construction of the predicate\\
@@
 - construction of the weak OT.
+
+The ``saturation'' step in the construction of the weak relation will
+pick all $\tau^*$ and $\tau^*;a$ sequences from the OA, and build a weak
+OT from each sequence. Here is one example:
 
@@
 $\qquad\ostate{2001}$ variables: $\psi_2 = \{r_1\_b:=r_0\_b; r_1\_m:=m;
-...\}$;\\
+; s_2\_b:=s_1\_b\}$;\\
 \\
@@
   \phi_3 = [v=out(r_1\_m)]}\ostate{2002}$\\
-$\qquad\ostate{2002}$ variables: $\psi_3 = \{r_2\_b:=r_1\_b\}$;\\
+$\qquad\ostate{2002}$ variables: $\psi_3 = \{r_2\_b:=r_1\_b; s_2\_b:=s_1\_b\}$;\\
 

### 2018-03-20 2016-Weak-FH-Bisim/WeakBisim.tex
Simplified version of Tr2

--- 2018-03-20 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 	synchronisation vector applicable to the rule subject, the premisses
-	include one {\em open transition} for each sub-pNet involved, one possible
+	include one {\em open transition} for each sub-pNet involved , one possible
 	{\em action} for each Hole involved, and the predicate relating these
-	with the resulting action of the vector.
+	with the resulting action of the vector. The sub-pNets involved are split between two 
+	sets, $I_2$ for subnets that are pLTSs, and $I_1$ for the others.
 	A key to understand this rule is that the open transitions are
@@
 	synchronisation vector.
-	\LUDO{now with two cases of induction} \LUDO{Why I'm and not Im?}
 	\begin{description}
@@
     $\inferrule
-    {k\!\in\! K \\SV_k \!=\! \SV{\alpha_m^{m \in I\uplus J}}{\alpha'}{e_b} \\
-    	Leaves(\mylangle \pNet_i^{i\in I'}, \overline{\Sort}, \symb{SV}_k^{k\in 
+    {k\!\in\! K \\SV_k \!=\! \SV{\alpha_m^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} \\
+    	Leaves(\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in 
     	K}\myrangle) \!=\! \pLTS_l^{l\in L} \\    	
-    	\forall m\!\!\in\!\! I. 	
-    {\left(\begin{array}{l}
-	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
+    	\forall m\!\!\in\!\! I_1. {\pNet_m \models\inferrule*[myfraction=\reddottedrule]
     	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m},
@@
     	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
-    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
-		{ \pNet_m 
+    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
+  \\
+\forall m\!\!\in\!\! I_2.		{ \pNet_m 
     	 \models
@@
     	{\ostate{s_m} \OTarrow {v_m}
-    		\ostate{s_m'}} \land I_m=\{m\} \land J_m=\emptyset}
-\end{array}\right)}\\
-    	%\land
-    	%Leaves(\pNet_m) = \overline{\pLTS}^{L_k})  	
-     J' = \biguplus_{m\in I}\!\! J_m \uplus J 	\\
-    	\Pred = \bigwedge_{m\in I}\!\! \Pred_m \land
-    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in I},b_j^{j\in J},v)\\ 
-    		I' = \biguplus_{m\in I}\!\! I_m
+    		\ostate{s_m'}} }
+\\ 	
+     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
+    	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
+    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in (I_1\uplus I_2)},b_j^{j\in J},v)\\ 
+    		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
     	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
@@
     }
-    {\mylangle \pNet_i^{i\in I'}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
+    {\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
     	\models
@@
    \begin{small}\begin{proof}
-       Consider each premise of the open transition (as constructed by rule TR2 in 
-       Definition~\ref{def:operationalSemantics}). 
+Consider rule TR2 in 
+       Definition~\ref{def:operationalSemantics}. 
 	\begin{description}
@@
 	\end{description}
-
 	\noindent
     $\inferrule
-    {k\!\in\! K \\SV_k \!=\! \SV{\alpha_m^{m \in I\uplus J}}{\alpha'}{e_b} \\
-    	Leaves(\mylangle \pNet_i^{i\in I'}, \overline{\Sort}, \symb{SV}_k^{k\in 
+    {k\!\in\! K \\SV_k \!=\! \SV{\alpha_m^{m \in I_1\uplus I_2\uplus 
+    J}}{\alpha'}{e_b} \\
+    	Leaves(\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in 
     	K}\myrangle) \!=\! \pLTS_l^{l\in L} \\    	
-    	\forall m\!\!\in\!\! I. 	
-    {\left(\begin{array}{l}
-	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
+    	\forall m\!\!\in\!\! I_1. {\pNet_m \models\inferrule*[myfraction=\reddottedrule]
     	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m},
@@
 
+Where $j_0\in I_1$ or $j_0\in I_2$
 We know each premise is true for $P[Q]_{j_0}$ and try to prove the equivalent premise for 
@@
 
-Now focus on OTs of the subnets. For each $m\in I\cup \{j_0\}$ we have one of the two 
+Now focus on OTs of the subnets. For each $m\in I_1\uplus I_2$ we have one of the two 
 following OT\footnotemark[\thefootnote]:\\[-2ex]
@@
     	{\ostate{s_m} \OTarrow {v_m}
-    		\ostate{s_m'}} \land I_m=\{m\} \land J_m=\emptyset}\]
+    		\ostate{s_m'}}}\]
 
 Only elements of $I$ are useful to assert the premise for reduction of $P$; the last 
-one ensures (note that $Q$ is at place $j_0$, and by definition of the open transition 
+one ensures the open transition for the pNet $Q$ (note that $Q$ is at place $j_0$, and by 
+definition of the open transition 
 for $P[Q]_{j_0}$, $I'_{j_0}=I\cap L_Q$, 
@@
 
-       Consider each premise of the open transition (constructed by Tr2 in 
+       Consider each premise of the open transition (constructed by \textbf{Tr2} in 
 Definition~\ref{def:operationalSemantics}). 
@@
 	are the 
-    set of leaves and holes of $P$, $I'$ and $J'$ are the sets of moving leaves and holes 
+    set of leaves and holes of $P$, $I_1\uplus I_2$ and $J'$ are the sets of moving 
+    leaves and holes 
     in the reduction of $P$. All sub-pNets of 
@@
     be 
-reduced:\\[-2ex]%\footnote{again we skip arguments related to renaming of fresh 
+reduced, we need:\\[-2ex]%\footnote{again we skip arguments related to renaming of fresh 
 %variables}:
-\[\forall m\!\!\in\!\! I\cup \{j_0\}. 	
-    {\left(\begin{array}{l}
-	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
+\[
+    	\forall m\!\!\in\!\! I_1\uplus\{j_0\}. {\pNet_m 
+    	\models\inferrule*[myfraction=\reddottedrule]
     	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m},
@@
     	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
-    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
-		{ \pNet_m 
+    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
+  \]\[
+\forall m\!\!\in\!\! I_2.		{ \pNet_m 
     	 \models
@@
     	{\ostate{s_m} \OTarrow {v_m}
-    		\ostate{s_m'}} \land I_m=\{m\} \land J_m=\emptyset}
-\end{array}\right)}\]
+    		\ostate{s_m'}} }\]
+%\forall m\!\!\in\!\! I\cup \{j_0\}. 	
+%    {\left(\begin{array}{l}
+%	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
+%    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m},
+%    	\{\xrightarrow{b_{j}}_j\}^{j\in J_m}, \Pred_m, \Post_m}
+%    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
+%    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
+%		{ \pNet_m 
+%    	 \models
+%    	\inferrule*[myfraction=\reddottedrule]
+%    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
+%    	{\ostate{s_m} \OTarrow {v_m}
+%    		\ostate{s_m'}} \land I_m=\{m\} \land J_m=\emptyset}
+%\end{array}\right)}\]
 the sub-pNet at position $j_0$ is the one filled by $Q$ which offers an open transition 
-by hypothesis.
+by hypothesis, the other open transitions are immediate consequence of the open 
+transition that can be performed by $P$ (premises of \textbf{Tr2}).
 Let $I''=\biguplus_{m\in I} I_m \uplus I_Q = I' \uplus I_Q$ and $J''= \biguplus_{m\in I} 

### 2018-03-20 2016-Weak-FH-Bisim/WeakBisim.tex
simpler OTs plus other remarks during meeting

@@
 	\label{def:OpenTransitions}
-	An \emph{open transition} over a set  $(S_i,s_{0 i}, \rightarrow_i)^{i\in
-	I}$ of LTSs, a
-	set $J$ of holes with sorts $\Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is 
+	An \emph{open transition} over a
+	set $J$ of holes with sorts $\Sort_j^{j\in J}$ and a set of states $\mathcal{S}$ is 
 	a structure of the form:	
@@
 	\inferrule*[myfraction=\reddottedrule]
-	{\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
-		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred, \Post}
+	{	\{b_j\}^{j\in J}, \Pred, \Post}
 	{s \OTarrow {v}s'}
 	\end{mathpar}
-	Where $s, s'\in\mathcal{S}$ and for all
-        $i\in I$, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the
-	LTS $(S_i,s_{0 i}, \rightarrow_i)$, and $\xrightarrow{b_j}_j$
+	Where $s, s'\in\mathcal{S}$ and $b_j$
         is a transition of the hole $j$, for any action $b_j$ in the
@@
 
+\TODO{rewrite example with new OTs}
 \begin{example}\emph{An open-transition.}
@@
 	An \emph{open automaton} is a structure\\ $A =
-	<\LTS_i^{i\in I},J,\mathcal{S},s_0,\mathcal{T}>$ where:
+	<J,\mathcal{S},s_0,\mathcal{T}>$ where:
 	\begin{itemize}
-		\item[$\bullet$]  $I$ and $J$ are  sets of indices,
-		\item[$\bullet$]  $\LTS_i^{i\in I}$ is a family of LTSs,
+		\item[$\bullet$]   $J$ is a  set of indices,
 		\item[$\bullet$]   $\mathcal{S}$ is a set of states and $s_0$ an initial state
@@
 		\item[$\bullet$] $\mathcal{T}$ is a set of open transitions and for each
-		$t\in \mathcal{T}$ there exist $I'$, $J'$ with $I'\subseteq I$, $J'
-		\subseteq J$, such that $t$ is an open transition over $\LTS_i^{i\in I'}$, $J'$,
+		$t\in \mathcal{T}$ there exist  $J'$ with  $J'
+		\subseteq J$, such that $t$ is an open transition over  $J'$,
 		and  $\mathcal{S}$.
@@
 	\label{def:operationalSemantics}
-	The semantics of a pNet $p$ is an open automaton $A = <Leaves(p),Holes(p),States(p),InitState(p),
+	The semantics of a pNet $p$ is an open automaton $A = 
+	<Holes(p),States(p),InitState(p),
 	\mathcal{T}>$ where $\mathcal{T}$ is the smallest set of open transitions		satisfying the rules below:
@@
 			\inferrule*[myfraction=\reddottedrule]
-			{\{s \xrightarrow{\alpha} s'\} ,\emptyset ,
+			{\emptyset ,
 			e_b,\left\{x_j\gets e_j\right\}^{j\in J}}
@@
 		}
-		$\LUDO {removed a ${}_p$ that was not bound}
+		$
 	\end{description}
@@
 	with the resulting action of the vector. The sub-pNets involved are split between two 
-	sets, $I_2$ for subnets that are pLTSs, and $I_1$ for the others.
+	sets, $I_2$ for subnets that are pLTSs, and $I_1$ for the others, $J$ is the set of 
+	holes involved in the transition\footnote{Formally, if $SV_k \!=\! \SV{\alpha_m^{m 
+	\in M}}{\alpha'}{e_b}$ is a synchronisation vector  of \pNet  then $K=M\cap 
+	\Holes(\pNet)$, $I_2=M\cap \Leaves(\pNet)$,  $I_1=M\setminus K \setminus 
+	I_2$}.
+
 	A key to understand this rule is that the open transitions are
@@
     $\inferrule
-    {k\!\in\! K \\SV_k \!=\! \SV{\alpha_m^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} \\
-    	Leaves(\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in 
-    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \\    	
+    {
 	\forall m\!\!\in\!\! I_1. {\pNet_m \models\inferrule*[myfraction=\reddottedrule]
-    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m},
-    	\{\xrightarrow{b_{j}}_j\}^{j\in J_m}, \Pred_m, \Post_m}
+    	{
+    	\{{b_{j}}\}^{j\in J_m}, \Pred_m, \Post_m}
     	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
     		\ostate{(s_i^\prime)^{i\in L_m}}} }	
-  \\
+  \qquad
 \forall m\!\!\in\!\! I_2.		{ \pNet_m 
@@
     	\inferrule*[myfraction=\reddottedrule]
-    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
+    	{\emptyset, \Pred_m, \Post_m}
     	{\ostate{s_m} \OTarrow {v_m}
-    		\ostate{s_m'}} }
+    		\ostate{s_m'}} }\\\\
+\Leaves(\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in 
+    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
+k\!\in\! K \qquad SV_k \!=\! \SV{\alpha_m^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} \\
 \\     	
@@
     }
-    {\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
+    {\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
     	\models
     	{\inferrule*[myfraction=\reddottedrule]
-    		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I^\prime},
-    		\{\xrightarrow{b_j}_j\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_k} 
+    		{
+    		\{{b_j}\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_1\uplus I_2} 
     		\Post_m}
@@
 \end{mathpar}
-  \caption{Proof of transition $OT_2$ (with interaction of processes $P$ and $Q$) for ``P>>(Q>>R)''}
+  \caption{Proof of transition $OT_2$ (with interaction of processes $P$ and $Q$) for 
+  ``P>>(Q>>R)'' \TODO{remove?}}
   \label{usingrules:OT2}
@@
 \begin{minipage}{0.69\linewidth} 	Suppose that
-   $A_1 = <\overline{\LTS_1},J,\mathcal{S}_1, s_0,
-   \mathcal{T}_1>$ and $A_2 = <\overline{\LTS_2},J,\mathcal{S}_2,t_0, \mathcal{T}_2>$
+   $A_1 = <J,\mathcal{S}_1, s_0,
+   \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0, \mathcal{T}_2>$
    are open automata where the set
@@
      \inferrule*[myfraction=\reddottedrule]
-         {\{s_i\xrightarrow{a_i}_i s'_i\}^{i\in I_1}, % , s_i,s'_i\in 
-         %States(I_1)
-           \{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
+         {
+           \{{b_j}\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
          {s \OTarrow {v} s'}
@@
     \inferrule*[myfraction=\reddottedrule]
-         {\{t_i\xrightarrow{a_{i x}}_i t_{i x}\}^{i\in I_{ x}},
-           \{\xrightarrow{b_{j x}}_j\}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {t \OTarrow {v_x} t_x}
-%         \right)
-\end{mathpar}
- such that  $\forall x, J_1=J_{x}, \exists \Pred_{s',t_x}. (s',t_x|\Pred_{s',t_x})\in 
- \mathcal{R}$; 
- and  \\
- $\Pred_{s,t} \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-   \left( \forall j. b_j=b_{jx}  \Rightarrow \Pred_{OT_x}
-     \land v\!=\!v_x \land  
-     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
-     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
-     %     \right)$.
-
-%     \TODO{Eric: j'ai ajoute $\exists$ sur les predicats $\Pred_{s',t_x}$, qui n'etaient pas definis...}
-
- \item  and symmetrically any open transition from $t$ in $\mathcal{T}_2$ can be 
-      covered by a set of transitions from $s$ in $\mathcal{T}_1$.
- \end{itemize}
-
-% \TODO{Eric: il reste des petits bugs genre $s^{2'}_x$ plutot que
-%   $s^{2}_x$}
-
-%Where $\symb{Subst}(\Pred,\Post)$ is the parallel substitution of all
-%assigned variables.
-Two pNets are FH-bisimilar if there exist a relation between their associated 
-automata that is an FH-bisimulation and their initial states are in the relation, i.e. 
-the predicate associated to the relation between the initial states is true.
-% \TODO{do we want formulas for this?}
- \end{definition}
-Classically, $\Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}$
-applies in parallel the  
-substitutions $\Post_{OT}$ and $\Post_{OT_x}$ (parallelism is crucial
-inside each $\Post$ set but $\Post_{OT}$ is independent from
-$\Post_{OT_x}$), applying the assignments of the involved rules.
-
-\medskip
-If we assume that everything is finite (states and transitions in the
-open automata, and the predicates in $\mathcal{R}$, then it is easy to
-prove that it is decidable whether a relation is a 
-FH-bisimulation, provided the logic of the predicates is decidable (see
-\cite{henrio:Forte2016}).
-
-\subsection{Post-processing: Elimination of intermediate variables}
-
-\ERIC{Optionally, simplify the predicate by eliminating the unnecessary intermediate variables, that were produced as fresh local variables of synchronisation vectors, and fresh result variables of intermediate OTs.
-In the resulting predicate the only significant variables are :\\
-- the input variables of pLTS transitions\\
-- the actions of holes\\
-- the result action at toplevel.}
-
-  \TODO{Eric: define ``elimination of intermediate variables ?'' it
-    transforms the predicates, it is not an
-    ``equivalence'' transformation, rather some sort of
-    abstraction... Does it change the satisfiability ?}
-
-\subsection{Running example}
-
-\TODO{Eric: full result of the tool execution on the running
-  example. Full ? certainly not, just a subset...}
-
-\section{Bisimulation}
-\label{section:bisimulation}
-
-	Now we use our symbolic operational semantics to define a notion of
-	strong (symbolic) bisimulation. Moreover this equivalence is decidable whenever we 
-	have some
-	decision procedure on the predicates of the action algebra.
-
-%% , that we prove compatible with the
-%% composition of open pNets. \TODO{do we really know this ?}
-
-The equivalence we need is a strong bisimulation between
-pNets having exactly the same Holes with the same sorts, but using a
-flexible matching 
-between open transition, to accommodate comparisons between pNet
-expressions with different architectures.
- We name it FH-bisimulation,
- as a short cut for the ``Formal Hypotheses'' manipulated in the
- transitions, but also as a reference to the work of De Simone~\cite{deSimone85},
- that pioneered this idea.
-
-Let $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$ be a relation over the set $\mathcal{S}_1$ and 
-$\mathcal{S}_2$ constrained by a predicate.
-More precisely, for any pair $(s,t)$, there is a 
-   single
-      $(s,t|\Pred_{s,t})\in\mathcal{R}$  stating that $s$ and $t$ are related 
-      if $\Pred_{s,t}$ 
-      is 
-      true, i.e. the states are related when the variables in $s$ and $t$ verify the 
-      predicate $\Pred_{s,t}$.
- FH-bisimulation is defined formally: 
- \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim}
-
-\noindent
-\begin{minipage}{0.69\linewidth} 	Suppose that
-   $A_1 = <\overline{\LTS_1},J,\mathcal{S}_1, s_0,
-   \mathcal{T}_1>$ and $A_2 = <\overline{\LTS_2},J,\mathcal{S}_2,t_0, \mathcal{T}_2>$
-   are open automata where the set
-   of holes are equal 
-   and of the same sort.
-
- Then 
-$\mathcal{R}$ is an FH-bisimulation iff for any  states
-$s\in\mathcal{S}_1$ and $t\in\mathcal{S}_2$, $(s,t|\Pred_{s,t})\in\mathcal{R}$, we 
-have
-the following:
-\end{minipage}
-\hspace{2mm}
-\begin{minipage}{0.30\linewidth}
-	\includegraphics[width=\linewidth]{XFIG/Bisim}
-%	\TODO{J'ai ajoute les predicats. Il reste a dessiner la ``couverture'' si j'y arrive...}
-\end{minipage}
-
- \begin{itemize}
- \item  For any open transition $OT$ in $\mathcal{T}_1$:
- \begin{mathpar}
-     \inferrule*[myfraction=\reddottedrule]
-         {\{s_i\xrightarrow{a_i}_i s'_i\}^{i\in I_1}, % , s_i,s'_i\in 
-         %States(I_1)
-           \{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
-         {s \OTarrow {v} s'}
-
-\end{mathpar}
- there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
- \begin{mathpar}
-%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
-    \inferrule*[myfraction=\reddottedrule]
-         {\{t_i\xrightarrow{a_{i x}}_i t_{i x}\}^{i\in I_{ x}},
-           \{\xrightarrow{b_{j x}}_j\}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {
+           \{{b_{j x}}\}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
          {t \OTarrow {v_x} t_x}
@@
  \inferrule*[myfraction=\reddottedrule]
-         {\{s_i\xrightarrow{a_i}_i s'_i\}^{i\in I_1}, 
-           \{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred,\Post}
+         {
+           \{{b_j}\}^{j\in J_1},\Pred,\Post}
          {s \OTWeakarrow {v} s'}
@@
      \inferrule*[myfraction=\reddottedrule]
-         {\{s_i\xrightarrow{a_i}_i s'_i\}^{i\in I_1},
-           \{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
+         {
+           \{{b_j}\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
          {s \OTarrow {v} s'}
@@
     \inferrule*[myfraction=\reddottedrule]
-         {\{t_i\xrightarrow{a_{i x}}_i t_{i x}\}^{i\in I_{x}},
-           \{\xrightarrow{b_{j x}}_j\}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {
+           \{{b_{j x}}\}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
          {t \OTWeakarrow {v_x} t_x}
@@
        	\inferrule*[myfraction=\reddottedrule]
-       	{\{s_i\xrightarrow{a_i}_i {s}'_i\}^{i\in I_1}, % , s^1_i,s^{1'}_i\in
-       		%States(I_1)
-       		\{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
+       	{
+       		\{{b_j}\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
        	{s \OTarrow {v} {s}'}
@@
        	\inferrule*[myfraction=\reddottedrule]
-       	{\{t_{p i}\xrightarrow{a_{p i x}}_i t_{p i x}\}^{i\in I_{p x}},
-       		\{\xrightarrow{b_{j p x}}_j\}^{j\in J_{px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
+       	{
+       		\{{b_{j p x}}\}^{j\in J_{px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
        	{t_p \OTarrow {v_{px}} t_{p x}}
@@
        	\inferrule*[myfraction=\reddottedrule]
-       	{\{u_i\xrightarrow{a_{i p x y}}_i u_{i p x y}\}^{i\in I_{p x y}},
-       		\{\xrightarrow{b_{j p x y}}_j\}^{j\in J_{pxy}}, 
+       	{
+       		\{{b_{j p x y}}\}^{j\in J_{pxy}}, 
        		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
@@
 		{\inferrule*[myfraction=\reddottedrule]
-			{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I},
-				\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred,  
+			{
+				\{{b_j}\}^{j\in J}, \Pred,  
 				\Post}
@@
 		P\models{\inferrule*[myfraction=\reddottedrule]
-			{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I\setminus L_Q},
-				\{\xrightarrow{b_j}_j\}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
+			{
+				\{{b_j}\}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
 				\Pred\,',  
@@
 		Q\models{\inferrule*[myfraction=\reddottedrule]
-			{\{s_i\xrightarrow{a_i}_i s_i'\}^{\,i\in I\cap L_Q},
-				\{\xrightarrow{b_j}_j\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
+			{
+				\{\xrightarrow{b_j}\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
 				\Post\,''}
@@
     $\inferrule
-    {k\!\in\! K \\SV_k \!=\! \SV{\alpha_m^{m \in I_1\uplus I_2\uplus 
-    J}}{\alpha'}{e_b} \\
-    	Leaves(\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in 
-    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \\    	
+    {
 	\forall m\!\!\in\!\! I_1. {\pNet_m \models\inferrule*[myfraction=\reddottedrule]
-    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m},
-    	\{\xrightarrow{b_{j}}_j\}^{j\in J_m}, \Pred_m, \Post_m}
+    	{
+    	\{{b_{j}}\}^{j\in J_m}, \Pred_m, \Post_m}
     	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
     		\ostate{(s_i^\prime)^{i\in L_m}}} }	
-  \\
+  \qquad
 \forall m\!\!\in\!\! I_2.		{ \pNet_m 
@@
 \pNet_m \models\inferrule*[myfraction=\reddottedrule]
-    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m},
-    	\{\xrightarrow{b_{j}}_j\}^{j\in J_m}, \Pred_m, \Post_m}
+    	{
+    	\{{b_{j}}\}^{j\in J_m}, \Pred_m, \Post_m}
     	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
@@
     	\inferrule*[myfraction=\reddottedrule]
-    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
+    	{\emptyset, \Pred_m, \Post_m}
     	{\ostate{s_m} \OTarrow {v_m}
@@
 	\[Q\models{\inferrule*[myfraction=\reddottedrule]
-		{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I\cap L_Q},
-			\{\xrightarrow{b_j}_j\}^{j\in J\cap\Holes(Q)}, \Pred_{j_0},  
+		{
+			\{{b_j}\}^{j\in J\cap\Holes(Q)}, \Pred_{j_0},  
 			\Post\,''}
@@
 choose\footnotemark[\thefootnote]  $v_Q=v_{j_0}$ ($\Pred\,''= \Pred_{j_0}$). Considering 
-the OT of $P$ let $I'= 
-\biguplus I_m=I\setminus L_Q$, $J'=\biguplus J_m\uplus J
-\uplus\{j_0\}=J\setminus\Holes(Q)\uplus \{j_0\}$;  the predicate is 
+the OT of $P$ we have  $I'_P=I'\setminus L_Q$, and $J'_P=J'\setminus\Holes(Q)\uplus 
+\{j_0\}$;  the predicate is 
 $\Pred\,'=\bigwedge_{m\in I_k}\Pred_m  \land \Pred_{\symb{sv}}(SV_k,v_m^{m\in 
@@
 v=\alpha'
-\land g$. Modulo renaming of fresh variables, this is identical to the predicate that 
+\land e_b$. Modulo renaming of fresh variables, this is identical to the predicate that 
 occurs in 
@@
 P\models{\inferrule*[myfraction=\reddottedrule]
-	{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I},
-		\{\xrightarrow{b_j}_j\}^{j\in J}, \\\\
+	{
+		\{{b_j}\}^{j\in J}, 
 		\Pred,  
@@
 }%\]
-\text{~and~}
+\text{~~and~~}
 %\[
 Q\models{\inferrule*[myfraction=\reddottedrule]
-	{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I_Q},
-		\{\xrightarrow{b_j}_j\}^{j\in J_Q},\\\\
+	{
+		\{{b_j}\}^{j\in J_Q},
 		 \Pred\,',  
@@
 	{\inferrule*[myfraction=\reddottedrule]
-		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I \uplus I_Q},
-			\{\xrightarrow{b_j}_j\}^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
+		{
+			\{{b_j}\}^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
 			\Pred\subst{b_{j_0}\leftarrow v_Q}\land\Pred\,',  
@@
     	\models\inferrule*[myfraction=\reddottedrule]
-    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m},
-    	\{\xrightarrow{b_{j}}_j\}^{j\in J_m}, \Pred_m, \Post_m}
+    	{
+    	\{{b_{j}}\}^{j\in J_m}, \Pred_m, \Post_m}
     	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
@@
 transition that can be performed by $P$ (premises of \textbf{Tr2}).
-Let $I''=\biguplus_{m\in I} I_m \uplus I_Q = I' \uplus I_Q$ and $J''= \biguplus_{m\in I} 
-J_m \uplus J_Q \uplus J = J'\setminus\{j_0\}\uplus J_Q$. The predicate for the open 
-transition is: $\Pred\,''=\bigwedge_{m\in I}\Pred_m \land \Pred\,'
+The set of moving leaves is the union of the moving leaves in the open transition for $P$ 
+and the ones for $Q$: 
+$I'_{PQ}= I'_P \uplus I'_Q$, similarly the moving holes are the union of the moving 
+holes, minus $j_0$: $J'_{PQ}=  J\setminus\{j_0\}\uplus J_Q$. The 
+predicate for the open 
+transition is: $\Pred\,''=\bigwedge_{m\in I _1\uplus I_2}\Pred_m \land \Pred\,'
 \land \Pred(SV_k,a_i^{i\in I_k}\uplus(j_0\mapsto v_Q),b_j^{j\in J},v)$. By definition 
@@
  \[P[Q]_{j_0}\models\inferrule*[myfraction=\reddottedrule]
- {\{s_i\xrightarrow{a_i}_i s'_i\}^{i\in I}, % , s^1_i,s^{1'}_i\in 
- 	%States(I_1)
- 	\{\xrightarrow{b_j}_j\}^{j\in J},\Pred_{OT},\Post_{OT}}
+ {
+ 	\{{b_j}\}^{j\in J},\Pred_{OT},\Post_{OT}}
  { \ostate{s_{i}^{i \in L_P\uplus L}}\OTarrow {v} \ostate{{s'}_{i}^{~i \in 
@@
  P\models{\inferrule*[myfraction=\reddottedrule]
- 	{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I\setminus L},
- 		\{\xrightarrow{b_j}_j\}^{j\in J'}, 
+ 	{
+ 		\{{b_j}\}^{j\in J'}, 
  		\Pred\,',  
@@
  Q\models{\inferrule*[myfraction=\reddottedrule]
- 	{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I\cap L},
- 		\{\xrightarrow{b_j}_j\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
+ 	{
+ 		\{\xrightarrow{b_j}\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
  		\Post\,''}
@@
  Q'\models\inferrule*[myfraction=\reddottedrule]
- {\{t_{i}\xrightarrow{a_{i x}}_i t_{i x}\}^{i\in I_{x}},
- 	\{\xrightarrow{b_{j x}}_j\}^{j\in J\cap\Holes(Q)}, 
+ {
+ 	\{\xrightarrow{b_{j x}}\}^{j\in J\cap\Holes(Q)}, 
  	\Pred_{OT_x},\Post_{OT_x}}
@@
  {\inferrule*[myfraction=\reddottedrule]
- 	{\{t_{i}\xrightarrow{a_{i x}}_i {t}_{i x}\}^{i\in I_x \uplus 
- 			(I\cap L_P)},
- 		\{\xrightarrow{b_{j x}}_j\}^{j\in J}, \\
+ 	{
+ 		\{{b_{j x}}\}^{j\in J}, 
  		\Pred\,'\subst{b_{j_0 x}\leftarrow v_x}\land\Pred_{OT_x},  
@@
 	\[P[Q]_{j_0}\models\inferrule*[myfraction=\reddottedrule]
-	{\{s_i\xrightarrow{a_i}_i s'_i\}^{i\in I}, % , s^1_i,s^{1'}_i\in 
-		%States(I_1)
-		\{\xrightarrow{b_j}_j\}^{j\in J},\Pred_{OT},\Post_{OT}}
+	{
+		\{{b_j}\}^{j\in J},\Pred_{OT},\Post_{OT}}
 	{ \ostate{s_{i}^{i \in L\uplus L_Q}}\OTarrow {v} \ostate{{s'}_{i}^{~i \in 
@@
 				P\models{\inferrule*[myfraction=\reddottedrule]
-				{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I\setminus L_Q},
-					\{\xrightarrow{b_j}_j\}^{j\in J'}, 
+				{
+					\{{b_j}\}^{j\in J'}, 
 					\Pred\,',  
@@
 			Q\models{\inferrule*[myfraction=\reddottedrule]
-				{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I\cap L_Q},
-					\{\xrightarrow{b_j}_j\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
+				{
+					\{{b_j}\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
 					\Post\,''}
@@
 			P'\models\inferrule*[myfraction=\reddottedrule]
-			{\{t_{i}\xrightarrow{a_{i x}}_i t_{i x}\}^{i\in I_{x}},
-				\{\xrightarrow{b_{j x}}_j\}^{j\in J'}, 
+			{
+				\{{b_{j x}}\}^{j\in J'}, 
 				\Pred_{OT_x},\Post_{OT_x}}
@@
 				{\inferrule*[myfraction=\reddottedrule]
-					{\{t_{i}\xrightarrow{a_{i x}}_i {t}_{i x}\}^{i\in I_x \uplus 
-					(I\cap L_Q)},
-						\{\xrightarrow{b_{j x}}_j\}^{j\in J}, \\
+					{
+						\{{b_{j x}}\}^{j\in J}, 
 						\Pred_{OT_x}\subst{b_{j_0 x}\leftarrow v_Q}\land\Pred\,'',  

### 2018-03-23 2016-Weak-FH-Bisim/WeakBisim.tex
c est pas K c est J dans la footnote
small changes to OTs
2 new fashion OTs in page 6 & 7

--- 2018-03-20 2016-Weak-FH-Bisim/WeakBisim.tex
@@
  \includegraphics[width=4.5cm]{XFIG/TransportSpec}
-  \caption{Schema and specification of the protocol }  \label{schema:ABP-pnets}
+  \caption{\TODO{Replace by various versions of the media} }  \label{schema:ABP-pnets}
 %\end{minipage}
@@
 %\begin{minipage}{6cm}
-  \centerline{\includegraphics[width=11cm]{XFIG/ABP3-Schema}}
+  \centerline{\includegraphics[width=11cm]{XFIG/ABP4-Schema}}
   \caption{Composed pNet with the ABP protocol}  \label{schema:ABP-composed}
@@
   \label{OT:ABP}
-  The \texttt{ABP} pNet of Fig. \ref{schema:ABP-composed} has 2 controllers and 2 holes. One of its possible open-transition is:
+  The \texttt{Protocol} pNet of Fig. \ref{schema:ABP-composed} has 4 controllers and no holes. One of its possible open-transition (the sender sending $m,b$ to the medium) is:
 
@@
  $  OT_2  = \openrule{
-                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
-                            \xrightarrow{in(?m,?b)}_{M1}
+%                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
+   %                           \xrightarrow{in(?m,?b)}_{M1}
+      \emptyset; Pred=[m=s_1\_m, b=s_1\_sb];  Post=\{m_1\_m:=m, m_1\_b:=b\}
                       }
   %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
-    { \OTarrow{\ostate{1,0,0,0}\underline{send(m,b)}} \ostate{2,1,0,0}}
+    {Prot_1 \OTarrow{\tau} Prot_2}
+  $
+
+At the upper level, the $ABP$ pNet has 2 holes and and $Protocol$ has a subnet. One of its possible transition (synchronizing the hole $P$ with the $Protocol$) is:
+ \smallskip
+ $  OT_1  = \openrule{
+%                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
+%                            \xrightarrow{in(?m,?b)}_{M1}
+      \{\xrightarrow{send(m)}_P\}; Pred=True; Post=\{s1\_m:=m\}
+                      }
+  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
+    {ABP_1 \OTarrow{\underline{send(m)}} ABP_2}
   $
@@
 	holes involved in the transition\footnote{Formally, if $SV_k \!=\! \SV{\alpha_m^{m 
-	\in M}}{\alpha'}{e_b}$ is a synchronisation vector  of \pNet  then $K=M\cap 
-	\Holes(\pNet)$, $I_2=M\cap \Leaves(\pNet)$,  $I_1=M\setminus K \setminus 
+	\in M}}{\alpha'}{e_b}$ is a synchronisation vector  of \pNet\  then $J=M\cap 
+	\Holes(\pNet)$, $I_2=M\cap \Leaves(\pNet)$,  $I_1=M\setminus J \setminus 
 	I_2$}.

### 2018-03-26 2018-Arch-pNets/arch-pNets.tex
Now compiles :)
WEAK: removed a TODO and added a TODO section at the begining
Clean up the notation paragraph

@@
 
-We extensively use \replaceSB{indexed structures
+We extensively use indexed structures
 over some countable indexed sets, which are equivalent to mappings over
-the countable set. }{structures indexed over some finite or countable sets of indices, which can be equivalently defined as mappings over such index sets. }% . The indexes will usually be
-% integers, bounded or not. Such an indexed family is
-%denoted
-%follows:
-\addSB{Thus, }
+the countable set. 
+Thus, 
 $a_i^{i\in I}$
@@
 % (arithmetic only appears in the indexes if necessary).
-\replaceSB{$a_i^{i\in I}$ }{This notation }defines both $I$ the set over which the family is
+This notation defines both $I$ the set over which the family is
 indexed (called \emph{range}), and $a_i$ the elements of the family.
@@
 ambiguous, we shall use notations for sets, and typically write
-``indexed set over I''\replaceSB{ when}{, even though} formally we should speak of multisets; and
+``indexed set over I'', even though formally we should speak of multisets; and
 write $x\in a_i^{i\in I}$ to mean $\exists i\in I.\, x=a_i$.  An empty
-family is denoted $\emptyset$. \replaceSB{
-We denote classically with an overline -- $\overline{a}$ -- a family when the indexing set 
-is
-not meaningful.}{We use a classical overline notation, \eg $\overline{a}$, for a family, where the indexing set is irrelevant} \replaceSB{$\uplus$ is }{Finally, we use $\uplus$ to denote }the disjoint union on
+family is denoted $\emptyset$. We use a classical overline notation, \eg $\overline{a}$, 
+for a family, where the indexing set is irrelevant. Finally, we use $\uplus$ to denote 
+the disjoint union on
 indexed sets.
@@
 
+\todoLH{Guard syntax???}
 \begin{definition}[pNets]\label{def-pnets}
@@
 is said to be \emph{open}.
-
+\end{itemize}
+\end{definition}
 \subsection{Operational Semantics for Open pNets}

### 2018-03-26 2016-Weak-FH-Bisim/WeakBisim.tex
New mathpartir => more space between line AND reformat all rules due to change of alignment!
Changed Fig 1

--- 2018-03-23 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 assignments. Without loss of generality and to simplify the formalisation, we suppose 
-here that 
-variables are local to each 
+here that variables are local to each 
 state: each state has its set of variables disjoint from the others. Transmitting 
@@
 
-  \includegraphics[width=7cm]{XFIG/Transport}
+ %%  \includegraphics[width=7cm]{XFIG/Transport}
+ %%  \hspace{0.5cm}
+ %% \includegraphics[width=4.5cm]{XFIG/TransportSpec}
+ %%  \caption{\TODO{Replace by various versions of the media} }  \label{schema:ABP-pnets}
+
+  \centerline{
+   \includegraphics[width=3.5cm]{XFIG/PerfectMedium}
    \hspace{0.5cm}
- \includegraphics[width=4.5cm]{XFIG/TransportSpec}
-  \caption{\TODO{Replace by various versions of the media} }  \label{schema:ABP-pnets}
+   \includegraphics[width=4cm]{XFIG/FaultyMedium}
+   }
+   \caption{Perfect and faulty (loosing and duplicating) media}  \label{schema:ABP-media}
+
   %\end{minipage}
@@
 
-\TODO{rewrite example with new OTs}
+\TODO{Add somewhere a subsection ``running example'' ?}
+
+%%\TODO{rewrite example with new OTs}
 \begin{example}\emph{An open-transition.}
@@
 			\models
-			\inferrule*[myfraction=\reddottedrule]
+			\mprset{myfraction=\reddottedrule}\inferrule
 			{\emptyset ,
@@
 	The second rule deals with pNet nodes: for each possible
-	synchronisation vector applicable to the rule subject, the premisses
+	synchronisation vector (of index $k$) applicable to the rule subject, the premisses
 	include one {\em open transition} for each sub-pNet involved , one possible
@@
 
-	A key to understand this rule is that the open transitions are
-	expressed in terms of the leaves and holes of the pNet structure,
-	i.e. a flatten view of the pNet: e.g. $L$ is the index set of the
-	Leaves, $L_m$ the index set of the leaves of one subnet indexed $m$, so all $L_m$
-	are disjoint subsets of $L$. Thus the states in the open transitions,
-	at each level, are tuples including states of all the
-	leaves of the pNet, not only those involved in the chosen
-	synchronisation vector.
 	\begin{description}
@@
 	\noindent
-    $\inferrule
+\begin{mathpar}
+    \mprset {vskip=1ex}
+\inferrule
     {
-	\forall m\!\!\in\!\! I_1. {\pNet_m \models\inferrule*[myfraction=\reddottedrule]
+\Leaves(\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in 
+    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
+k\!\in\! K \qquad SV_k \!=\! \SV{\alpha_m^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} \\
+\\     	
+	\forall m\!\!\in\!\! I_1. {\pNet_m 
+	\models\mprset{myfraction=\reddottedrule}\inferrule
     	{
@@
     	 \models
-    	\inferrule*[myfraction=\reddottedrule]
+    	\mprset{myfraction=\reddottedrule}\inferrule
     	{\emptyset, \Pred_m, \Post_m}
@@
     		\ostate{s_m'}} }\\\\
-\Leaves(\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in 
-    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
-k\!\in\! K \qquad SV_k \!=\! \SV{\alpha_m^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} \\
-\\     	
      J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
@@
     	\models
-    	{\inferrule*[myfraction=\reddottedrule]
+    	{\mprset{myfraction=\reddottedrule}\inferrule
     		{
@@
     }
-    $
+\end{mathpar}    
 	\medskip
@@
 	%%include it, because it may change the decidability conditions on predicates}
+
+        	A key to understand this rule is that the open transitions are
+	expressed in terms of the leaves and holes of the pNet structure,
+	i.e. a flatten view of the pNet: e.g. $L$ is the index set of the
+	Leaves, $L_m$ the index set of the leaves of one subnet indexed $m$, so all $L_m$
+	are disjoint subsets of $L$. Thus the states in the open transitions,
+	at each level, are tuples including states of all the
+	leaves of the pNet, not only those involved in the chosen
+	synchronisation vector.
 
@@
 		\models
-		{\inferrule*[myfraction=\reddottedrule]
+		{\mprset{myfraction=\reddottedrule}\inferrule
 			{
@@
 		\begin{mathpar}
-		P\models{\inferrule*[myfraction=\reddottedrule]
+		P\models{\mprset{myfraction=\reddottedrule}\inferrule
 			{
@@
 		%\[
-		Q\models{\inferrule*[myfraction=\reddottedrule]
+		Q\models{\mprset{myfraction=\reddottedrule}\inferrule
 			{
@@
     {
-	\forall m\!\!\in\!\! I_1. {\pNet_m \models\inferrule*[myfraction=\reddottedrule]
+	\forall m\!\!\in\!\! I_1. {\pNet_m \models\mprset{myfraction=\reddottedrule}\inferrule
     	{
@@
 \[
-\pNet_m \models\inferrule*[myfraction=\reddottedrule]
+\pNet_m \models\mprset{myfraction=\reddottedrule}\inferrule
     	{
@@
 $L_{j_0}=L_Q$, and $J_{j_0}=	J\cap\Holes(Q)$):\\[-2ex]
-	\[Q\models{\inferrule*[myfraction=\reddottedrule]
+	\[Q\models{\mprset{myfraction=\reddottedrule}\inferrule
 		{
@@
 %\[
-P\models{\inferrule*[myfraction=\reddottedrule]
+P\models{\mprset{myfraction=\reddottedrule}\inferrule
 	{
@@
 %\[
-Q\models{\inferrule*[myfraction=\reddottedrule]
+Q\models{\mprset{myfraction=\reddottedrule}\inferrule
 	{
@@
 	\models
-	{\inferrule*[myfraction=\reddottedrule]
+	{\mprset{myfraction=\reddottedrule}\inferrule
 		{
@@
     	\forall m\!\!\in\!\! I_1\uplus\{j_0\}. {\pNet_m 
-    	\models\inferrule*[myfraction=\reddottedrule]
+    	\models\mprset{myfraction=\reddottedrule}\inferrule
     	{
@@
  \\[-2ex]     
- \[P[Q]_{j_0}\models\inferrule*[myfraction=\reddottedrule]
+ \[P[Q]_{j_0}\models\mprset{myfraction=\reddottedrule}\inferrule
  {
@@
  	\begin{mathpar}
- P\models{\inferrule*[myfraction=\reddottedrule]
+ P\models{\mprset{myfraction=\reddottedrule}\inferrule
  	{
@@
  }\\
- Q\models{\inferrule*[myfraction=\reddottedrule]
+ Q\models{\mprset{myfraction=\reddottedrule}\inferrule
  	{
@@
  \begin{mathpar}
- Q'\models\inferrule*[myfraction=\reddottedrule]
+ Q'\models\mprset{myfraction=\reddottedrule}\inferrule
  {
@@
  \models
- {\inferrule*[myfraction=\reddottedrule]
+ {\mprset{myfraction=\reddottedrule}\inferrule
  	{
@@
 \\[-2ex]     
-	\[P[Q]_{j_0}\models\inferrule*[myfraction=\reddottedrule]
+	\[P[Q]_{j_0}\models\mprset{myfraction=\reddottedrule}\inferrule
 	{
@@
 			\begin{mathpar}
-				P\models{\inferrule*[myfraction=\reddottedrule]
+				P\models{\mprset{myfraction=\reddottedrule}\inferrule
 				{
@@
 			}\\
-			Q\models{\inferrule*[myfraction=\reddottedrule]
+			Q\models{\mprset{myfraction=\reddottedrule}\inferrule
 				{
@@
 			%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
-			P'\models\inferrule*[myfraction=\reddottedrule]
+			P'\models\mprset{myfraction=\reddottedrule}\inferrule
 			{
@@
 				\models
-				{\inferrule*[myfraction=\reddottedrule]
+				{\mprset{myfraction=\reddottedrule}\inferrule
 					{

### 2018-03-26 2018-Arch-pNets/arch-pNets.tex
Updated the model (definitions) to include priorities

--- 2018-03-07 2018-Arch-pNets/arch-pNets.tex
@@
 \newcommand{\exprs}[1]{\ensuremath{\sE_{#1}}}
+\newcommand{\boolexprs}[1]{\ensuremath{\sB_{#1}}}
 \newcommand{\assigns}[1]{\ensuremath{\sA_{#1}}}
@@
 \newcommand{\val}[3][]{\ensuremath{#1{\sigma}^{#2}_{#3}}}
+
+\newcommand{\filter}[2][]{\ensuremath{\pi_{#1}({#2})}}
 
@@
     \\
-    \guards{\#1} &
-    {\ttfamily\textbackslash guards\{\#1\}} &
-    {\ttfamily\textbackslash sB\^{}\{<\}\{\#1\}}
-    \\
     \exprs{\#1} &       
@@
     {\ttfamily\textbackslash sE\_\{\#1\}}
+    \\
+    \boolexprs{\#1} &       
+    {\ttfamily\textbackslash boolexprs\{\#1\}} &
+    {\ttfamily\textbackslash sB\_\{\#1\}}
+    \\
+    \guards{\#1} &
+    {\ttfamily\textbackslash guards\{\#1\}} &
+    {\ttfamily\textbackslash sB\^{}\{<\}\_\{\#1\}}
     \\
@@
 \emph{data expressions} $\exprs{\variables}$ \replaceSB{, including}{and} a set of \emph{Boolean
-expressions} \todoLH{$\mathcal{B} \to g$}
+expressions} \todoLH{$\mathcal{B} \to g$}\todoSB{change to $\boolexprs{\variables}$?}
 $\guards{\variables}$ ($\guards{\variables}\subseteq\exprs{\variables}$).
@@
     is a \emph{transition relation}, with transitions
-    labelled by triples consisting of an \emph{interaction}
+    labelled by \emph{interactions}, \ie triples consisting of a non-empty set of ports
     $\emptyset \neq a \subseteq P$, a monotonic Boolean \emph{guard} $g \in
@@
 %
-  We call \noteSB{Maybe rather $(P, \export)$}\hl{the pair of sets $(V,P)$} the \emph{interface} of the
+  We call the triple $(V,P, \export)$ the \emph{interface} of the
   component.\,\footnote{%
@@
   Notations $q \goesto{a} q'$ and $q \goesto{a}$ are as usual;
-  for a component $B$, we denote $Q_B$, $q^0_B$, $P_B$, $V_B$ and
-  $\val{0}{B}$ the corresponding constituents of $B$.  We will
+  for a component $B$, we denote $Q_B$, $q^0_B$, $V_B$, $\val{0}{B}$, $P_B$,
+  and $\export[B]$ the corresponding constituents of $B$.  We will
   skip the index on the transition relations $\goesto{}$, since it
@@
   The \emph{open semantics} of a component $B = (Q, q^0, V,
-  \val{0}{}, P, \export, \goesto{})$ is given by the LTS $\semopen{B} = (S,
+  \val{0}{}, P, \export, \goesto{})$ is given by the LTS denoted $\semopen{B} = (S,
   s^0, \goesto{})$, where $S = Q \times \valuations{V}$, $s^0 =
@@
   \todoSB{Do we actually need this?}
-  \hl{The \emph{closed semantics} of $B$ is given by the LTS
+  \hl{The \emph{closed semantics} of $B$ is given by the LTS denoted
   $\semclosed{B} \bydef{=}\reachable{\semopen{B}}$, comprising
@@
 
-\begin{definition}[Interaction model \& composition]
+\begin{definition}[Interaction model]
   \label{defn:im}
-  Consider a finite set of components $\cB = (Q_i, q^0_i, V_i,
-  \val{0}{i}, P_i, \export[i], \goesto{})^{i \in I}$, such that
-  all their respective components (\ie $Q_i$, $P_i$, and $V_i$)
-  are pairwise disjoint, \ie $\forall i \neq j,\ Q_i \cap Q_j =
-  P_i \cap P_j = V_i \cap V_j = \emptyset$.  Let $P = \bigcup_{i
-  \in I} P_i$ and $V = \bigcup_{i \in I} V_i$.
+  Consider a finite set of component interfaces $(V_i, P_i,
+  \export[i])^{i \in I}$, such that all $P_i$ and all $V_i$ are
+  pairwise disjoint, \ie $\forall i \neq j,\ P_i \cap P_j = V_i \cap
+  V_j = \emptyset$.  Let $P = \bigcup_{i \in I} P_i$, $V = \bigcup_{i
+    \in I} V_i$ and $\export : P \rightarrow 2^V$ such that, for any
+  $p \in P_i$, $\export(p) = \export[i](p)$.
 %
@@
   \bydef{=} \setdef{i \in I}{a \cap P_i \neq \emptyset}$ the
-  \emph{support} of $a$,
-  \noteSB{Updated this}\hl{and $V_a \bydef{=} \bigcup_{i \in
-    \supp{a}} \export[i](a \cap P_i)$ the set of component
-  variables exported for $a$.}
-
-  An \emph{interaction model over \hl{$(V,P)$}} is a set $\Gamma
+  \emph{support} of $a$.
+  %% \noteSB{Updated this}\hl{and $V_a \bydef{=} \bigcup_{i \in
+  %%   \supp{a}} \export[i](a \cap P_i)$ the set of component
+  %% variables exported through $a$.}
+
+  An \emph{interaction model over \hl{$(V, P, \export)$}} is a set $\Gamma
   \subseteq 2^P \times \guards{V} \times \exprs{V}$, such that,
-  for any $(a, g, e) \in \Gamma$, the guard and update expression
-  associated to the \emph{interaction} $a$ satisfy, respectively,
-  $g \in \guards{V_a}$ and $e \in \exprs{V_a}$.\footnote{%
+  for any interaction $(a, g, e) \in \Gamma$, we have
+  $g \in \guards{\export(a)}$ and $e \in \exprs{\export(a)}}$.\footnote{%
 %
@@
   %% interaction model.
-
-  The \emph{composition of $\cB$ with the interaction model
-    $\Gamma$} is the component
-  $\Gamma(\cB) = (Q, q^0, V, \val{0}{}, P, \export, \goesto{})$,
-  where
+\end{definition}
+
+\begin{definition}[Composition]
+  \label{defn:im:sem}
+  The \emph{composition} of a finite set of components $\cB = (Q_i,
+  q^0_i, V_i, \val{0}{i}, P_i, \export[i], \goesto{})^{i \in I}$ with
+  the interaction model $\Gamma$ over $(V_i, P_i, \export[i])^{i \in
+    I}$ is the component $\Gamma(\cB) = (Q, q^0, V, \val{0}{}, P,
+    \export, \goesto{})$, where
 %
@@
   V_i$, $\val{0}{}(v) = \val{0}{i}(v)$;
-%
-  $\export : P \rightarrow 2^V$ is such that, for any $p \in
-  P_i$, $\export(p) = \export[i](p)$;
 %
@@
 %%     \\[0.5\baselineskip]
-    \label{eq:im:int}
+    \label{eq:im:sem}
 %
@@
   \end{gather}
+  \todoSBin{Add the intuitive explanation}
 \end{definition}
 
-Below, when speaking of a set of components $\cB$, we will always
-assume that it satisfies all the assumptions of \defn{im}.
-%
-For an interaction $a$, we will abuse the notation by writing
+Below, when speaking of a set of components $\cB$ or interfaces, we will always
+assume that it satisfies the disjointness assumption of \defn{im}.
+%
+For a set of ports $a$, we will abuse the notation by writing
 $\supp{a}$ to also denote the set $\setdef{B \in \cB}{a \cap P_B
@@
 always be clear from the context.
+
+\begin{definition}[Priority model]
+  \label{defn:priority}
+  A \emph{priority model} over a component interface $(V, P,
+  \export{})$ is a strict partial order on interactions: $\pi
+  \subseteq \bigl(2^P \times \guards{V} \times \exprs{V} \bigr)^2.
+
+  We denote $\filter{\alpha} \bydef{=} \setdefb{\beta \in (2^P \times
+    \guards{V} \times \exprs{V})}{\alpha \prec_\pi \beta}$ the set of
+  interactions that have higher priority than $\alpha$.
+\end{definition}
+
+\begin{definition}[Application of priority]
+  \label{defn:priority:sem}
+  The application of a priority model $\pi$ over $(V, P, \export{})$
+  to a component $B = (Q, q^0, V, \val{0}{}, P, \export, \goesto{})$
+  is the component $\pi(B) = (Q, q^0, V, \val{0}{}, P, \export,
+  \goesto[\pi]{})$, where $\goesto[\pi]{}$ is the minimal transition
+  relation satisfying the rule
+%
+  \begin{equation}
+    \label{eq:priority:sem}
+%
+    \infer{    
+      q \goesto{a, g, e} q'
+      \and
+      \textstyle
+      g' = g \land \bigwedge_{(b, h, f) \in \filter[q]{\alpha}} \lnot h
+    }{
+      q \goesto{a, g', e} q'
+    }\,, 
+  \end{equation}
+%
+  where $\filter[q]{\alpha} \bydef{=} \filter{\alpha} \cap
+  \setdefb{\beta \in (2^P \times \guards{V} \times \exprs{V})}{q
+    \goesto{\beta}}$.
+  \todoSBin{Add the intuitive explanation}
+\end{definition}
+
+In this paper, we will only consider the so-called \emph{maximal
+  progress} priority, where $(a, g, e) \prec (b, h, f)$ iff $a
+\varsubsetneq b$ (\ie $a \subseteq b$ and $a \neq b$).  In
+\secn{conclusion}, we discuss the possibility of generalising the
+obtained results to other priority models.
 

### 2018-03-26 2018-Arch-pNets/arch-pNets.tex
Minor clean-up in the use of the macro \export

@@
   A \emph{component} is a tuple $(Q, q^0, V, \val{0}{}, P,
-  \export{}, \goesto{})$, where
+  \export, \goesto{})$, where
   \begin{itemize}
@@
   for any interaction $(a, g, e) \in \Gamma$, we have
-  $g \in \guards{\export(a)}$ and $e \in \exprs{\export(a)}}$.\footnote{%
+  $g \in \guards{\export(a)}$ and $e \in \exprs{\export(a)}$.\footnote{%
 %
@@
   A \emph{priority model} over a component interface $(V, P,
-  \export{})$ is a strict partial order on interactions: $\pi
-  \subseteq \bigl(2^P \times \guards{V} \times \exprs{V} \bigr)^2.
+  \export)$ is a strict partial order on interactions: $\pi
+  \subseteq \bigl(2^P \times \guards{V} \times \exprs{V} \bigr)^2$.
 
@@
   \label{defn:priority:sem}
-  The application of a priority model $\pi$ over $(V, P, \export{})$
+  The application of a priority model $\pi$ over $(V, P, \export)$
   to a component $B = (Q, q^0, V, \val{0}{}, P, \export, \goesto{})$
@@
   \label{defn:arch}
-  An \emph{architecture} is a tuple $A = (\cC, V_A, P_A, \Gamma)$,
+  An \emph{architecture} is a tuple $A = (\cC, V_A, P_A, \export[A], \Gamma)$,
   where $\cC$ is a finite set of \emph{coordinating components}
@@
   $\Gamma \subseteq 2^{P_A} \times \guards{V_A} \times \exprs{V_A}$
-  is an interaction model over \hl{$(V_A, P_A)$}.
+  is an interaction model over \hl{$(V_A, P_A, \export[A])$}.
 \end{definition}

### 2018-03-26 2018-Arch-pNets/arch-pNets.tex
More clean-up

@@
   q^0_i, V_i, \val{0}{i}, P_i, \export[i], \goesto{})^{i \in I}$ with
-  the interaction model $\Gamma$ over $(V_i, P_i, \export[i])^{i \in
-    I}$ is the component $\Gamma(\cB) = (Q, q^0, V, \val{0}{}, P,
+  the interaction model $\Gamma$ over $(V, P, \export)$ (as in \defn{im})
+  is the component $\Gamma(\cB) = (Q, q^0, V, \val{0}{}, P,
     \export, \goesto{})$, where
@@
 %
-      G = g \land \bigwedge_{i \in \supp{a}} g_i
-      \and
-      E = e; e_i^{i \in \supp{a}}
+      g' = g \land \bigwedge_{i \in \supp{a}} g_i
+      \and
+      e' = e; e_i^{i \in \supp{a}}
     }{
-      (q_i)^{i \in I} \goesto{a, G, E} (q_i')^{i \in I}
+      (q_i)^{i \in I} \goesto{a, g', e'} (q_i')^{i \in I}
     }\,.
@@
   A \emph{priority model} over a component interface $(V, P,
-  \export)$ is a strict partial order on interactions: $\pi
+  \export)$\footnote{%
+%
+    Notice that the export function $\export$ has no impact on the
+    priority model definition.
+%
+  } is a strict partial order on interactions: $\pi
   \subseteq \bigl(2^P \times \guards{V} \times \exprs{V} \bigr)^2$.
@@
 
+\begin{note}
+  Below, we will assume that the maximal progress priority is
+  implicitly applied after each composition with an interaction model.
+\end{note}
+
 %****************************************************************
@@
   $\bigcup_{C \in \cC} P_C \subseteq P_A$ and
-  $\bigcup_{C \in \cC} V_C \subseteq V_A$, and
+  $\bigcup_{C \in \cC} V_C \subseteq V_A$;
+%
+  $\export[A] : P_A \rightarrow 2^{V_A}$ is an export function, such
+  that $\export[A](p) = \export[C](p)$, for any $C \in \cC$ and $p \in
+  P_C$ and $\export[A](p) \subseteq V_A \setminus \bigcup_{C \in \cC}
+  V_C$ for any $p \in P_A \setminus \bigcup_{C \in \cC} P_C$; and
+%
   $\Gamma \subseteq 2^{P_A} \times \guards{V_A} \times \exprs{V_A}$
@@
   \label{defn:arch:application}
-  Let $A = (\cC, V_A, P_A, \Gamma)$ be an architecture and let $\cB$
+  Let $A = (\cC, V_A, P_A, \export[A], \Gamma)$ be an architecture and let $\cB$
   be a set of components, such that
@@
 %
-  and
-  %% , denoting, for any $(a, g, e) \in \Gamma$, $V_a \bydef{=}
-  %% \bigcup_{B \in \supp{a}} \export[B](a \cap P_B)$, we have
-  $g \in \guards{V_a}$ and
-  $e \in \exprs{V_a}$ (see \defn{im} for the notation $V_a$).
+  \hl{and $\export[A](p) = V_A \cap \export[B](p)$, for any $B \in \cB$
+  and $p \in P_A \cap P_B$.}
 %
@@
 An architecture $A$ enforces coordination constraints on the
-components in $\cB$.  The interface \hl{$(V_A, P_A)$} of an
+components in $\cB$.  The interface \hl{$(V_A, P_A, \export[A])$} of an
 architecture $A$ contains all ports of the coordinating

### 2018-03-26 2018-Arch-pNets/arch-pNets.tex
Added maximal progress everywhere, except the proofs

@@
 In this paper, we will only consider the so-called \emph{maximal
-  progress} priority, where $(a, g, e) \prec (b, h, f)$ iff $a
+  progress} priority $\mu$, where $(a, g, e) \prec_\mu (b, h, f)$ iff $a
 \varsubsetneq b$ (\ie $a \subseteq b$ and $a \neq b$).  In
@@
   Below, we will assume that the maximal progress priority is
-  implicitly applied after each composition with an interaction model.
+  applied after each composition with an interaction model.
 \end{note}
@@
   components $\cB$} is the component $ A(\cB) \bydef{=}
-  (\IMextend{\Gamma}{P})(\cC \cup \cB)$, where
+  \mu\bigl((\IMextend{\Gamma}{P})(\cC \cup \cB)\bigr)$, where
 %
@@
   denotes the \emph{extension} of the interaction model $\Gamma$
-  to the set of ports $P$.
+  to the set of ports $P$
+  and $\mu$ is the maximal progress priority model.
 \end{definition}
@@
   \label{defn:arch:composition}
-  Let $A_i = (\cC_i, V_{A_i}, P_{A_i}, \Gamma_i)$, for $i = 1,2$,
+  Let $A_i = (\cC_i, V_{A_i}, P_{A_i}, \export[A_i], \Gamma_i)$, for $i = 1,2$,
   be two architectures.  The \emph{composition} of $A_1$ and
   $A_2$ is the architecture $A_1 \arcomp A_2 = (\cC_1 \cup \cC_2,
-  V_{A_1} \cup V_{A_2}, P_{A_1} \cup P_{A_2}, \Gamma)$, where
+  V_{A_1} \cup V_{A_2}, P_{A_1} \cup P_{A_2}, \export[A_1] \cup \export[A_2], \Gamma)$, where
 %
@@
 %
-  Suppose we have two architectures $A = A'$.  This does not
+  Suppose we have two architectures $A \arequiv A'$.  This does not
   necessarily mean that their sets of coordinating components
@@
   \label{defn:impose}
-  Let $A = (\cC, P_A, V_A, \Gamma)$ be an architecture; let $\cB$
+  Let $A = (\cC, P_A, V_A, \export[A], \Gamma)$ be an architecture; let $\cB$
   be a set of components and $\Phi$ an initial property of
@@
   Let $\cB$ be a set of components; let $A_i = (\cC_i, V_{A_i},
-  P_{A_i}, \Gamma_i)$, for $i = 1,2$, be two architectures
+  P_{A_i}, \export[A_i], \Gamma_i)$, for $i = 1,2$, be two architectures
   enforcing on $\cB$ the properties $\Phi_1$ and $\Phi_2$

### 2018-03-27 2018-Arch-pNets/arch-pNets.tex

--- 2018-03-26 2018-Arch-pNets/arch-pNets.tex
@@
 \newcommand{\exprs}[1]{\ensuremath{\sE_{#1}}}
-\newcommand{\boolexprs}[1]{\ensuremath{\sB_{#1}}}
 \newcommand{\assigns}[1]{\ensuremath{\sA_{#1}}}
@@
 \newcommand{\val}[3][]{\ensuremath{#1{\sigma}^{#2}_{#3}}}
-
-\newcommand{\filter}[2][]{\ensuremath{\pi_{#1}({#2})}}
 
@@
 
-\replaceSB{Our models rely }{The pNet model in \secn{pNets} relies }on a notion of parameterised actions, that are
-symbolic expressions using data types and variables. As \replaceSB{our model aims }{we aim }at encoding the low-level behaviour of possibly very different
+\noteLHin{I believe we should simplify this paragraph about param actions}
+The pNet model in \secn{pNets} relies on a notion of parameterised actions, that are
+symbolic expressions using data types and variables. As we aim at encoding the low-level 
+behaviour of possibly very different
 programming languages, we do not want to impose one specific algebra
@@
     \\
+    \guards{\#1} &
+    {\ttfamily\textbackslash guards\{\#1\}} &
+    {\ttfamily\textbackslash sB\^{}\{<\}\{\#1\}}
+    \\
     \exprs{\#1} &       
@@
     {\ttfamily\textbackslash sE\_\{\#1\}}
-    \\
-    \boolexprs{\#1} &       
-    {\ttfamily\textbackslash boolexprs\{\#1\}} &
-    {\ttfamily\textbackslash sB\_\{\#1\}}
-    \\
-    \guards{\#1} &
-    {\ttfamily\textbackslash guards\{\#1\}} &
-    {\ttfamily\textbackslash sB\^{}\{<\}\_\{\#1\}}
     \\
@@
 \emph{data expressions} $\exprs{\variables}$ \replaceSB{, including}{and} a set of \emph{Boolean
-expressions} \todoLH{$\mathcal{B} \to g$}\todoSB{change to $\boolexprs{\variables}$?}
+expressions} \todoLH{$\mathcal{B} \to g$}
 $\guards{\variables}$ ($\guards{\variables}\subseteq\exprs{\variables}$).
@@
   A \emph{component} is a tuple $(Q, q^0, V, \val{0}{}, P,
-  \export, \goesto{})$, where
+  \export{}, \goesto{})$, where
   \begin{itemize}
@@
     is a \emph{transition relation}, with transitions
-    labelled by \emph{interactions}, \ie triples consisting of a non-empty set of ports
+    labelled by triples consisting of an \emph{interaction}
     $\emptyset \neq a \subseteq P$, a monotonic Boolean \emph{guard} $g \in
@@
 %
-  We call the triple $(V,P, \export)$ the \emph{interface} of the
+  We call \noteSB{Maybe rather $(P, \export)$}\hl{the pair of sets $(V,P)$} the \emph{interface} of the
   component.\,\footnote{%
@@
   Notations $q \goesto{a} q'$ and $q \goesto{a}$ are as usual;
-  for a component $B$, we denote $Q_B$, $q^0_B$, $V_B$, $\val{0}{B}$, $P_B$,
-  and $\export[B]$ the corresponding constituents of $B$.  We will
+  for a component $B$, we denote $Q_B$, $q^0_B$, $P_B$, $V_B$ and
+  $\val{0}{B}$ the corresponding constituents of $B$.  We will
   skip the index on the transition relations $\goesto{}$, since it
@@
   The \emph{open semantics} of a component $B = (Q, q^0, V,
-  \val{0}{}, P, \export, \goesto{})$ is given by the LTS denoted $\semopen{B} = (S,
+  \val{0}{}, P, \export, \goesto{})$ is given by the LTS $\semopen{B} = (S,
   s^0, \goesto{})$, where $S = Q \times \valuations{V}$, $s^0 =
@@
   \todoSB{Do we actually need this?}
-  \hl{The \emph{closed semantics} of $B$ is given by the LTS denoted
+  \hl{The \emph{closed semantics} of $B$ is given by the LTS
   $\semclosed{B} \bydef{=}\reachable{\semopen{B}}$, comprising
@@
 
-\begin{definition}[Interaction model]
+\begin{definition}[Interaction model \& composition]
   \label{defn:im}
-  Consider a finite set of component interfaces $(V_i, P_i,
-  \export[i])^{i \in I}$, such that all $P_i$ and all $V_i$ are
-  pairwise disjoint, \ie $\forall i \neq j,\ P_i \cap P_j = V_i \cap
-  V_j = \emptyset$.  Let $P = \bigcup_{i \in I} P_i$, $V = \bigcup_{i
-    \in I} V_i$ and $\export : P \rightarrow 2^V$ such that, for any
-  $p \in P_i$, $\export(p) = \export[i](p)$.
+  Consider a finite set of components $\cB = (Q_i, q^0_i, V_i,
+  \val{0}{i}, P_i, \export[i], \goesto{})^{i \in I}$, such that
+  all their respective components (\ie $Q_i$, $P_i$, and $V_i$)
+  are pairwise disjoint, \ie $\forall i \neq j,\ Q_i \cap Q_j =
+  P_i \cap P_j = V_i \cap V_j = \emptyset$.  Let $P = \bigcup_{i
+  \in I} P_i$ and $V = \bigcup_{i \in I} V_i$.
 %
@@
   \bydef{=} \setdef{i \in I}{a \cap P_i \neq \emptyset}$ the
-  \emph{support} of $a$.
-  %% \noteSB{Updated this}\hl{and $V_a \bydef{=} \bigcup_{i \in
-  %%   \supp{a}} \export[i](a \cap P_i)$ the set of component
-  %% variables exported through $a$.}
-
-  An \emph{interaction model over \hl{$(V, P, \export)$}} is a set $\Gamma
+  \emph{support} of $a$,
+  \noteSB{Updated this}\hl{and $V_a \bydef{=} \bigcup_{i \in
+    \supp{a}} \export[i](a \cap P_i)$ the set of component
+  variables exported for $a$.}
+
+  An \emph{interaction model over \hl{$(V,P)$}} is a set $\Gamma
   \subseteq 2^P \times \guards{V} \times \exprs{V}$, such that,
-  for any interaction $(a, g, e) \in \Gamma$, we have
-  $g \in \guards{\export(a)}$ and $e \in \exprs{\export(a)}$.\footnote{%
+  for any $(a, g, e) \in \Gamma$, the guard and update expression
+  associated to the \emph{interaction} $a$ satisfy, respectively,
+  $g \in \guards{V_a}$ and $e \in \exprs{V_a}$.\footnote{%
 %
@@
   %% interaction model.
-\end{definition}
-
-\begin{definition}[Composition]
-  \label{defn:im:sem}
-  The \emph{composition} of a finite set of components $\cB = (Q_i,
-  q^0_i, V_i, \val{0}{i}, P_i, \export[i], \goesto{})^{i \in I}$ with
-  the interaction model $\Gamma$ over $(V_i, P_i, \export[i])^{i \in
-    I}$ is the component $\Gamma(\cB) = (Q, q^0, V, \val{0}{}, P,
-    \export, \goesto{})$, where
+
+  The \emph{composition of $\cB$ with the interaction model
+    $\Gamma$} is the component
+  $\Gamma(\cB) = (Q, q^0, V, \val{0}{}, P, \export, \goesto{})$,
+  where
 %
@@
   V_i$, $\val{0}{}(v) = \val{0}{i}(v)$;
+%
+  $\export : P \rightarrow 2^V$ is such that, for any $p \in
+  P_i$, $\export(p) = \export[i](p)$;
 %
@@
 %%     \\[0.5\baselineskip]
-    \label{eq:im:sem}
+    \label{eq:im:int}
 %
@@
   \end{gather}
-  \todoSBin{Add the intuitive explanation}
 \end{definition}
 
-Below, when speaking of a set of components $\cB$ or interfaces, we will always
-assume that it satisfies the disjointness assumption of \defn{im}.
-%
-For a set of ports $a$, we will abuse the notation by writing
+Below, when speaking of a set of components $\cB$, we will always
+assume that it satisfies all the assumptions of \defn{im}.
+%
+For an interaction $a$, we will abuse the notation by writing
 $\supp{a}$ to also denote the set $\setdef{B \in \cB}{a \cap P_B
@@
 
-\begin{definition}[Priority model]
-  \label{defn:priority}
-  A \emph{priority model} over a component interface $(V, P,
-  \export)$ is a strict partial order on interactions: $\pi
-  \subseteq \bigl(2^P \times \guards{V} \times \exprs{V} \bigr)^2$.
-
-  We denote $\filter{\alpha} \bydef{=} \setdefb{\beta \in (2^P \times
-    \guards{V} \times \exprs{V})}{\alpha \prec_\pi \beta}$ the set of
-  interactions that have higher priority than $\alpha$.
-\end{definition}
-
-\begin{definition}[Application of priority]
-  \label{defn:priority:sem}
-  The application of a priority model $\pi$ over $(V, P, \export)$
-  to a component $B = (Q, q^0, V, \val{0}{}, P, \export, \goesto{})$
-  is the component $\pi(B) = (Q, q^0, V, \val{0}{}, P, \export,
-  \goesto[\pi]{})$, where $\goesto[\pi]{}$ is the minimal transition
-  relation satisfying the rule
-%
-  \begin{equation}
-    \label{eq:priority:sem}
-%
-    \infer{    
-      q \goesto{a, g, e} q'
-      \and
-      \textstyle
-      g' = g \land \bigwedge_{(b, h, f) \in \filter[q]{\alpha}} \lnot h
-    }{
-      q \goesto{a, g', e} q'
-    }\,, 
-  \end{equation}
-%
-  where $\filter[q]{\alpha} \bydef{=} \filter{\alpha} \cap
-  \setdefb{\beta \in (2^P \times \guards{V} \times \exprs{V})}{q
-    \goesto{\beta}}$.
-  \todoSBin{Add the intuitive explanation}
-\end{definition}
-
-In this paper, we will only consider the so-called \emph{maximal
-  progress} priority, where $(a, g, e) \prec (b, h, f)$ iff $a
-\varsubsetneq b$ (\ie $a \subseteq b$ and $a \neq b$).  In
-\secn{conclusion}, we discuss the possibility of generalising the
-obtained results to other priority models.
-
 %****************************************************************
@@
   \label{defn:arch}
-  An \emph{architecture} is a tuple $A = (\cC, V_A, P_A, \export[A], \Gamma)$,
+  An \emph{architecture} is a tuple $A = (\cC, V_A, P_A, \Gamma)$,
   where $\cC$ is a finite set of \emph{coordinating components}
@@
   $\Gamma \subseteq 2^{P_A} \times \guards{V_A} \times \exprs{V_A}$
-  is an interaction model over \hl{$(V_A, P_A, \export[A])$}.
+  is an interaction model over \hl{$(V_A, P_A)$}.
 \end{definition}

### 2018-03-27 2016-Weak-FH-Bisim/WeakBisim.tex
definition of plts and pnets without sorts and with notations

--- 2018-03-26 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 \begin{itemize}
-\item[$\bullet$] $I \in \I$ is the set over which sub-pNets are indexed.
-\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets.
+\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets indexed over $I \in \I$.
 %  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which sub-pNets are indexed.
@@
   \item The sort of a pNet is its signature, i.e. the set of actions it can
-perform. In the definition of sorts, we do not need to distinguish
-input variables (that specify the dataflow within LTSs), so for
-computing LTS sorts, we use a substitution operator\footnote{$\subst{y_k\gets x_k}^{k\in K}$ is the parallel substitution 
-operation.} to remove the
-\emph{input marker} of variables. Formally:
+perform, where each action signature is an action 
+label plus the arity of the action. In the definition of sorts, we do not need to 
+distinguish
+input variables and we remove the
+\emph{input marker} of variables.
 \[
@@
 \item
-The set of holes of a pNet is defined inductively; the sets of holes
-in a pNet node and its subnets are all disjoint:
+The set of holes $\Holes(\pNet_{i_1})$ of a pNet is the indexes of the holes of the pNet 
+itself plus the indexes of all the holes of its subnets.
+It is defined inductively (we suppose those indexes 
+disjoints):
   \[\begin{array}{l}
@@
 \item
-The set of leaves of a pNet is the set of all pLTSs occurring in the structure, defined 
-inductively as:
+The set of leaves of a pNet is the set of all pLTSs occurring in the structure, as an 
+indexed family of the form $\Leaves(\pNet)= \mylangle \pNet_i \myrangle^{i \in L}$.
 \[\begin{array}{l}

### 2018-03-27 2018-Arch-pNets/arch-pNets.tex
definition of plts and pnets without sorts and with notations

@@
 
-A pLTS is a labelled transition system with variables\replaceSB{; variables}{. Variables} can be
-manipulated, defined, or accessed \noteSB{What does this mean?}\hl{inside states}, actions, guards, and
+A pLTS is a labelled transition system with variables. Variables can be
+used to characterise a state, as part of actions, guards, and
 assignments. Without loss of generality and to simplify the formalisation, we suppose 
@@
 %suppose that transitions looping to the same state does not do assignments.
-Note that we make no assumption on \addSB{the }finiteness of the set of states, nor
-on \addSB{the }finite branching of the transition relation.
+Note that we make no assumption on the finiteness of the set of states, nor
+on the finite branching of the transition relation.
 
@@
 \item[$\bullet$]
-$S$ is a set of states\addSB{, $\vars(s)$ denotes the set of associated variables}.
+$S$ is a set of states, $\vars(s)$ denotes the set of associated variables;
 \item[$\bullet$]
-$s_0 \in S$ is the initial state.\noteSB{I usually put commas or semicolons in itemised lists}
+$s_0 \in S$ is the initial state;
 %\item[$\bullet$]
@@
 % SB: I removed a new paragraph here, ok?
-$\langle \alpha,~g,~e\rangle$,
-where \noteSB{I suggest using $\actions{V}$ (\ie \texttt{\textbackslash actions\{V\}}), with $V = \bigcup_{s \in S} \vars(s)$.}\hl{$\alpha \in\AlgA$} is a parameterised action, $g$ is a guard, and \hl{the variables
-$x_j\in \vars(s')$
-are assigned the updates in $e$.
-}\noteSB{I still have to update in my section, but it seems that my initial use of expressions conflicts with that in the SVs.
-I suggest writing explicitly $(?x_i := e_i)^{i \in I}$ or $\overline{?x := e}$ (not sure these should be input vars, though).}
+$\langle \alpha,~g,~u\rangle$,
+where $\alpha$ is a parameterised action, $\alpha \in\actions{\variables}$; 
+$g\in\boolexprs{\variables}$ is a guard over variables of the source state and the 
+action, and $u\in\assigns{\variables}$
+assigns updated value for variables in the destination state. 
 If 
-$s \xrightarrow{\langle \alpha,~g,~e\rangle} s'\in \to $ then 
+$s \xrightarrow{\langle \alpha,~g,~u\rangle} s'\in \to $ then 
 % REMOVED BECAUSE USELESS: $\iv(\alpha)\!\subseteq\! \vars(s')$, 
@@
 		$\vars(g)\!\subseteq\! \vars(s)\cup\vars(\alpha)$, and
-		$\vars(\codom(e))\!\subseteq\! \vars(s)\cup\vars(\alpha)\land 
-		\vars(\dom(e))\!\in\!\vars(s')$. %,  and $s= s'\Rightarrow J=\emptyset$.
+		$\vars(\codom(u))\!\subseteq\! \vars(s)\cup\vars(\alpha)\land 
+		\vars(\dom(u))\!\in\!\vars(s')$. %,  and $s= s'\Rightarrow J=\emptyset$.
 
@@
 \begin{itemize}
-\item[$\bullet$] \noteSB{This is clear from $\pNet_i^{i\in I}$.}\hl{$I \in \I$ is the set over which sub-pNets are indexed.}
-\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets.
+\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets;
 %  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which 
@@
 
-\item[$\bullet$] \noteSB{$I_P$ is not defined and, probably, not necessary.}\hl{$J\!\in\!\I_\P$} is a set of indexes, called \emph{holes}.
+\item[$\bullet$] $J$ is a set of indexes, called \emph{holes}.
 $I$ and $J$ are \emph{disjoint}: $I\!\cap\! J=\emptyset$,  $I\!\cup\! J\neq\emptyset$
@@
   \symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k\,|\,g_k$, where
-  $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
-  $\forall i\!\in\!
-  I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$,  $\forall j\!\in\!
-  J_k.\,\alpha_{j}\!\in\!\Sort_j$, and $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
+  $\alpha'_k\in \actions{\variables}$, $I_k\subseteq I$, $J_k\subseteq J$, and 
+  $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
   J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
-\replaceSB{$\Label(\symb{SV}_k) = \alpha'_k$}{$\alpha'_k$, also denoted $\Label(\symb{SV}_k)$}. \replaceSB{$g_k $ is a guard associated to the vector 
-$\vars(g_k)\subseteq \bigcup_{l\in I_k\uplus J_k}{\vars({\alpha_l})}$.}{The Boolean expression $g_k $, such that $\vars(g_k)\subseteq \bigcup_{l\in I_k\uplus J_k}{\vars({\alpha_l})}$, is a guard associated to the vector.}
+$\alpha'_k$. The Boolean expression $g_k $, such that $\vars(g_k)\subseteq \bigcup_{l\in 
+I_k\uplus J_k}{\vars({\alpha_l})$, is a guard associated to the vector.}
 
 \end{itemize}
-\end{definition}
-
-The preceding definition relies on the auxiliary functions below:
-
-\begin{definition}[Sorts, Holes, Leaves of pNets]
+We define the set of holes and leaves of a pNet as follows:
   \begin{itemize}
-  \item  \noteSB{I think this can be lightened up a bit, since the definitions are all straightforward, whereas the notation is complex.
-Maybe reformulate in words and move the formal definitions in the appendix?}
- The sort of a pNet is its signature, i.e. the set of actions it can
-perform.
-\noteSB{Is there any chance that, by writing assignments explicitly ($x := e$), we could eliminate the need to distinguish the input variables at all?
-That would simplify things.}\hl{In the definition of sorts, we do not need to distinguish
-input variables} (that specify the dataflow within LTSs), so for
-computing LTS sorts, we use a substitution operator\footnote{$\subst{y_k\gets x_k}^{k\in 
-K}$ is the parallel substitution 
-operation.} to remove the
-\emph{input marker} of variables. Formally:
-\[
-\begin{array}{l}
-\Sortop(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{x \gets ?x| 
-x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
-    J}\rangle} s'\in \to \} \\
-\Sortop(\mylangle \overline{\pNet}\!, %\pNet_i^{i\in I}, \Sort_j^{j\in J}
-\overline{\pNet}\!,
-\overline{\symb{SV}}\myrangle)
-=\{\alpha' |\, \overline{\alpha}%\alpha_j^{j\in J_k}
-\to\alpha'\in\set{\symb{SV}}\}
-\end{array}
-\]
-
-\item
-The set of holes of a pNet is defined inductively; the sets of holes
-in a pNet node and its subnets are all disjoint:
-  \[\begin{array}{l}
-\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset \\
-\Holes(\mylangle \pNet_i^{i\in I}\!,\Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) 
-=J\uplus{\displaystyle \bigcup_{i\in 
-I}\Holes(\pNet_i)}\\
-\forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
-\forall i_1,i_2\in I.\,i_1\neq i_2\Rightarrow  
-\Holes(\pNet_{i_1})\cap\Holes(\pNet_{i_2})=\emptyset
-\end{array}\]
-\item
-The set of leaves of a pNet is the set of all pLTSs occurring in the structure, defined 
-inductively as:
-\[\begin{array}{l}
-\Leaves(\mylangle S,s_0, \to\myrangle) \!=\!\{\mylangle S,s_0, \to\myrangle\}\\
-\Leaves(\mylangle \pNet_i^{i\in I}\!,%Sort_j^{j\in J}
-\overline{\Sort}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \biguplus_{i\in 
-I}\Leaves(\pNet_i)\uplus\{i\mapsto \pNet_i|\pNet_i\pNet_i \text{ is a }\pLTS\}}
-\end{array}\]
-\end{itemize}
-\end{definition}
-
-\noteLHin{Below a simpler def 11}
-\begin{definition}[Sorts, Holes, Leaves of pNets]
-  \begin{itemize}
-  \item 
- The sort of a pNet is its signature, i.e. the set of actions it can
-perform. A sort is a set of action signature, where each action signature is an action 
-label plus the arity of the action.
-
 \item
@@
 \end{itemize}
+A pNet $Q$ is \emph{closed} if it has no hole: $\Holes(Q)=\emptyset$; else it
+is said to be \emph{open}.
 \end{definition}
+
 \subsection{Operational Semantics for Open pNets}
@@
 	is verified and transforms assignments into post-conditions:
-
+	%%% compared to the other paper tguards and affectations should not be explicit
 	\begin{description}
@@
 
+\section{pNets additional definitions}
+\begin{definition}[Sorts, Holes, Leaves of pNets]
+  \begin{itemize}
+  \item  \noteSB{I think this can be lightened up a bit, since the definitions are all 
+  straightforward, whereas the notation is complex.  Maybe reformulate in words and move 
+  the formal definitions in the appendix?}
+ The sort of a pNet is its signature, i.e. the set of actions it can
+perform. \noteSB{Is there any chance that, by writing assignments explicitly ($x := e$), 
+we could eliminate the need to distinguish the input variables at all? That would 
+simplify things.}\hl{In the definition of sorts, we do not need to distinguish
+input variables} (that specify the dataflow within LTSs), so for
+computing LTS sorts, we use a substitution operator\footnote{$\subst{y_k\gets x_k}^{k\in 
+K}$ is the parallel substitution 
+operation.} to remove the
+\emph{input marker} of variables. Formally:
+\[
+\begin{array}{l}
+\Sortop(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{x \gets ?x| 
+x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
+    J}\rangle} s'\in \to \} \\
+\Sortop(\mylangle \overline{\pNet}\!, %\pNet_i^{i\in I}, \Sort_j^{j\in J}
+\overline{\pNet}\!,
+\overline{\symb{SV}}\myrangle)
+=\{\alpha' |\, \overline{\alpha}%\alpha_j^{j\in J_k}
+\to\alpha'\in\set{\symb{SV}}\}
+\end{array}
+\]
+
+\item
+The set of holes of a pNet is defined inductively; the sets of holes
+in a pNet node and its subnets are all disjoint:
+  \[\begin{array}{l}
+\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset \\
+\Holes(\mylangle \pNet_i^{i\in I}\!,\Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) 
+=J\uplus{\displaystyle \bigcup_{i\in 
+I}\Holes(\pNet_i)}\\
+\forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
+\forall i_1,i_2\in I.\,i_1\neq i_2\Rightarrow  
+\Holes(\pNet_{i_1})\cap\Holes(\pNet_{i_2})=\emptyset
+\end{array}\]
+\item
+The set of leaves of a pNet is the set of all pLTSs occurring in the structure, defined 
+inductively as:
+\[\begin{array}{l}
+\Leaves(\mylangle S,s_0, \to\myrangle) \!=\!\{\mylangle S,s_0, \to\myrangle\}\\
+\Leaves(\mylangle \pNet_i^{i\in I}\!,%Sort_j^{j\in J}
+\overline{\Sort}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \biguplus_{i\in 
+I}\Leaves(\pNet_i)\uplus\{i\mapsto \pNet_i|\pNet_i\pNet_i \text{ is a }\pLTS\}}
+\end{array}\]
+\end{itemize}
+\end{definition}
+
 \end{document}

### 2018-03-27 2016-Weak-FH-Bisim/WeakBisim.tex
desciption de l'ABP

@@
 \begin{figure}[t]
+  \centerline{
+   \includegraphics[width=8cm]{XFIG/ABP-Schema}
+   }
+   \caption{Schema of the ABP example}  \label{ABP:Schema}
+\end{figure}
+
+\begin{figure}[t]
 %\begin{minipage}{\linewidth}
@@
 \end{figure}
+
+\section{Running Example}
+To illustrate this work, we use the well-known Alternate bit protocol
+(ABP), that provides safe transport of data between two processes,
+over unsafe media. This protocol has been described and studied using
+many approaches, because it is small enough, and can be easily
+verified using exact finite models. Our version here is more
+ambitious, encoding both the data and the control bits in a symbolic
+way. One can imagine that this could easily be extended using bounded
+integers, as in the Sliding window protocol, or with more complex data
+structures, in order to verify realistic protocols.
+
+Fig. \ref{ABP:Schema} shows the example principle: two unspecified
+processes $P$ and $Q$ (Holes) communicate messages, with a data value
+argument, through the two protocol entities $sender$ and
+$receiver$. The underlying unsafe network is modelled by two media,
+carrying the message together with a control bit on one way, and an
+acknowledge back form $Q$ to $P$. The media can be perfect (safe), or
+faulty (losing or duplicating messages) as shown in
+Fig. \ref{schema:ABP-media}.
+
+The full system should be equivalent (e.g. through weak bisimulation)
+to the two processes connected simply through a perfect medium.
 

### 2018-03-27 2018-Arch-pNets/arch-pNets.tex
OOPS did not compile
again
changes in notations (unfinished)

@@
 $\alpha'_k$. The Boolean expression $g_k $, such that $\vars(g_k)\subseteq \bigcup_{l\in 
-I_k\uplus J_k}{\vars({\alpha_l})$, is a guard associated to the vector.}
+I_k\uplus J_k}{\vars({\alpha_l})}$, is a guard associated to the vector.
 
@@
 	\label{def:OpenTransitions}
-	An \emph{open transition} over a set \noteSB{In the architecture section, I say that we omit indices on $\goesto{}$ and that they are always clear from the context.}\hl{$(S_i,s_{0 i}, \rightarrow_i)^{i\in
-	I}$} of LTSs, a
-	set $J$ of holes with sorts $\Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is 
+	An \emph{open transition} over a
+	set $J$ of holes  and a set of states $\mathcal{S}$ is 
 	a structure of the form:	
@@
 	\inferrule*[myfraction=\reddottedrule]
-	{\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
-		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred, \Post}
+	{	\{\beta_j\}^{j\in J}, \Pred, \Post}
 	{s \OTarrow {v}s'}
 	\end{mathpar}
-	Where $s, s'\in\mathcal{S}$ and for all
-        $i\in I$, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the
-	LTS $(S_i,s_{0 i}, \rightarrow_i)$, and \noteSB{Why insist on ``transition'' and $\goesto{b_j}_j$? Why not simply ``$b_j$ is an action in the sort $\Sort_j$?}\hl{$\xrightarrow{b_j}_j$
-        is a transition of the hole $j$}, for any action $b_j$ in the
-        sort $\Sort_j$.
-\noteSB{Why $v$?
-Why not $\alpha$?
-As now, it is not clear whether this is an action term or a variable $v \in \vars(s)$ of some hypothetical state $s$.}\hl{$v$ is a variable denoting the resulting action}
+	Where $s, s'\in\mathcal{S}$ and $\beta_j\in\actions{\variables}$
+        is an action of the hole $j$. $v$ is a variable denoting the resulting action
         of this open transition. \Pred\ is a predicate 
 	over the different variables of the
-	terms, labels, and states $s_i$, $b_j$, $s$, $v$. \Post\ is a set of equations that 
-	hold \emph{after the open transition}, they are represented as a substitution of the 
-	form $\{x_k\gets \Expr_k\}^{k\in K}$ \noteLH{considering the level of abstraction I 
-	would like to just put $\Post_=e$}
-	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
-	variables of the open transition.
+	terms, labels, and states $s_i$, $\beta_j$, $s$, $v$. $\Post\in 
+	\assigns{\variables}$\ is 
+	a set of assignments that are the effects of the transition.
+\noteSB{Why $v$? Why not $\alpha$? As now, it is not clear whether this is an action term 
+or a variable $v \in \vars(s)$ of some hypothetical state $s$.}\hl{$v$ is a variable 
+denoting the resulting action}
 \end{definition}
+%\begin{definition}[Open transitions]
+%	\label{def:OpenTransitions}
+%	An \emph{open transition} over a set \noteSB{In the architecture section, I say that 
+%we omit indices on $\goesto{}$ and that they are always clear from the 
+%context.}\hl{$(S_i,s_{0 i}, \rightarrow_i)^{i\in
+%	I}$} of LTSs, a
+%	set $J$ of holes with sorts $\Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is 
+%	a structure of the form:	
+%	\begin{mathpar}
+%	\inferrule*[myfraction=\reddottedrule]
+%	{\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
+%		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred, \Post}
+%	{s \OTarrow {v}s'}
+%	\end{mathpar}
+%	Where $s, s'\in\mathcal{S}$ and for all
+%        $i\in I$, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the
+%	LTS $(S_i,s_{0 i}, \rightarrow_i)$, and \noteSB{Why insist on ``transition'' and 
+%$\goesto{b_j}_j$? Why not simply ``$b_j$ is an action in the sort 
+%$\Sort_j$?}\hl{$\xrightarrow{b_j}_j$
+%        is a transition of the hole $j$}, for any action $b_j$ in the
+%        sort $\Sort_j$.  
+%        of this open transition. \Pred\ is a predicate 
+%	over the different variables of the
+%	terms, labels, and states $s_i$, $b_j$, $s$, $v$. \Post\ is a set of equations that 
+%	hold \emph{after the open transition}, they are represented as a substitution of the 
+%	form $\{x_k\gets \Expr_k\}^{k\in K}$ \noteLH{considering the level of abstraction I 
+%	would like to just put $\Post_=e$}
+%	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
+%	variables of the open transition.
+%\end{definition}
 
@@
 	An \emph{open automaton} is a structure\\ $A =
-	\langle\LTS_i^{i\in I},J,\mathcal{S},s_0,\mathcal{T}\rangle$, where:
+	<J,\mathcal{S},s_0,\mathcal{T}>$ where:
 	\begin{itemize}
-		\item[$\bullet$]  $I$ and $J$ are  sets of indices,
-		\item[$\bullet$]  $\LTS_i^{i\in I}$ is a family of LTSs,
+		\item[$\bullet$]   $J$ is a  set of indices,
 		\item[$\bullet$]   $\mathcal{S}$ is a set of states and $s_0$ an initial state
@@
   \Pred_{\symb{sv}}(SV, 
-  a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow
+  \alpha_i^{i\in I}, \beta_j^{j\in J}, v)\Leftrightarrow
   \\
@@
 %% \begin{array}{l}
-\exists {\vars((a'_i)}^{i\in I}),
-{\vars((b'_j)}^{j\in J}),\vars(v').\, %SV=
+\exists {\vars((\alpha'_i)}^{i\in I}),
+{\vars((\beta'_j)}^{j\in J}),\vars(v').\, %SV=
 %\\
 %\land
-\\\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v' \land g
+\\\forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, \beta_j=\beta'_j \land 
+v=v' \land g
 %% \end{array} \bigg)
 \\
-\text{ Where } SV=\bigl({(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v' | g\bigr)
+\text{ Where } SV=\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}}{ v'}{ g}
 \end{multline}
@@
 	The semantics of a pNet $p$ is an open automaton $A = 
-	\langle\symb{Leaves}(p),\symb{Holes}(p),\symb{States}(p),\symb{InitState}(p),
-	\mathcal{T}\rangle$, where \noteSB{We use $\cT$ for term algebra}\hl{$\mathcal{T}$} is the smallest set of open transitions		
+	<Holes(p),States(p),InitState(p),
+	\mathcal{T}>$ where $\mathcal{T}$ is the smallest set of open transitions		
 	satisfying the rules below:
@@
 	is verified and transforms assignments into post-conditions:
-	%%% compared to the other paper tguards and affectations should not be explicit
+
 	\begin{description}
@@
 		$\inferrule
-		{ s \xrightarrow{\langle \alpha,~g,~e\rangle} s'\in \to  }
+		{ s \xrightarrow{\langle \alpha,~g,~u\rangle} s'\in \to  }
 		{ \mylangle  S,s_0, \to \myrangle
 			\models
-			\inferrule*[myfraction=\reddottedrule]
-			{\{s \xrightarrow{\alpha} s'\} ,\emptyset ,
-			g,e}
+			\mprset{myfraction=\reddottedrule}\inferrule
+			{\emptyset ,
+			g,u}
 			{\ostate{s} \OTarrow{\alpha} \ostate{s'}}
-		}$
+		}
+		$
 	\end{description}
@@
 	The second rule deals with pNet nodes: for each possible
-	synchronisation vector applicable to the rule subject, the premises
-	include one {\em open transition} for each sub-pNet involved, one possible
+	synchronisation vector (of index $k$) applicable to the rule subject, the premisses
+	include one {\em open transition} for each sub-pNet involved , one possible
 	{\em action} for each Hole involved, and the predicate relating these
-	with the resulting action of the vector.
-	A key to understand this rule is that the open transitions are
-	expressed in terms of the leaves and holes of the pNet structure,
-	i.e. a \noteSB{Is this compatible with the ``compositionality'' argument?}\hl{flattened view of the pNet}: e.g. $L$ is the index set of the
-	Leaves, $L_m$ the index set of the leaves of one subnet indexed $m$, so all $L_m$
-	are disjoint subsets of $L$. Thus the states in the open transitions,
-	at each level, are tuples including states of all the
-	leaves of the pNet, not only those involved in the chosen
-	synchronisation vector.
+	with the resulting action of the vector. The sub-pNets involved are split between two 
+	sets, $I_2$ for subnets that are pLTSs, and $I_1$ for the others, $J$ is the set of 
+	holes involved in the transition\footnote{Formally, if $SV_k \!=\! \SV{\alpha_m^{m 
+	\in M}}{\alpha'}{e_b}$ is a synchronisation vector  of \pNet\  then $J=M\cap 
+	\Holes(\pNet)$, $I_2=M\cap \Leaves(\pNet)$,  $I_1=M\setminus J \setminus 
+	I_2$}.
+
+	\begin{description}
+		\item[{\bf Tr2:}]
+	\end{description}
+
+	\noindent
+\begin{mathpar}
+    \mprset {vskip=1ex}
+\inferrule
+    {
+\Leaves(\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in 
+    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
+k\!\in\! K \qquad SV_k \!=\! \SV{\alpha_m^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{g} \\
+\\     	
+	\forall m\!\!\in\!\! I_1. {\pNet_m 
+	\models\mprset{myfraction=\reddottedrule}\inferrule
+    	{
+    	\{{b_{j}}\}^{j\in J_m}, \Pred_m, \Post_m}
+    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
+    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
+  \qquad
+\forall m\!\!\in\!\! I_2.		{ \pNet_m 
+    	 \models
+    	\mprset{myfraction=\reddottedrule}\inferrule
+    	{\emptyset, \Pred_m, \Post_m}
+    	{\ostate{s_m} \OTarrow {v_m}
+    		\ostate{s_m'}} }\\\\
+     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
+    	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
+    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in (I_1\uplus I_2)},b_j^{j\in J},v)\\ 
+    		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
+    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
+    {\tt fresh}(\alpha_m,\alpha',b_j,v) 
+    }
+    {\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
+    	\models
+    	{\mprset{myfraction=\reddottedrule}\inferrule
+    		{
+    		\{{b_j}\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_1\uplus I_2} 
+    		\Post_m}
+    		{\ostate{s_i^{i\in L}} \OTarrow {v}
+    			\ostate{(s_i^\prime)^{i\in L}}}
+    	}
+    }
+\end{mathpar}
+
 	\begin{description}
@@
 \Sortop(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{x \gets ?x| 
-x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
+x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~g,~(x_j\!:= {e}_j)^{j\in
     J}\rangle} s'\in \to \} \\

### 2018-03-27 2016-Weak-FH-Bisim/WeakBisim.tex
changes in notations (unfinished)
alphas and betas

@@
 	\inferrule*[myfraction=\reddottedrule]
-	{	\{b_j\}^{j\in J}, \Pred, \Post}
+	{	\{\beta_j\}^{j\in J}, \Pred, \Post}
 	{s \OTarrow {v}s'}
@@
 	over the different variables of the
-	terms, labels, and states $s_i$, $b_j$, $s$, $v$. \Post\ is a set of equations that 
+	terms, labels, and states $s_i$, $\beta_j$, $s$, $v$. \Post\ is a set of equations 
+	that 
 	hold \emph{after the open transition}, they are represented as a substitution of the 
@@
 the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
-\[\Pred_{\symb{sv}}(SV, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow \bigg(
+\[\Pred_{\symb{sv}}(SV, \alpha_i^{i\in I}, \beta_j^{j\in J}, v)\Leftrightarrow \bigg(
 \begin{array}{l}
-\exists {(a'_i)}^{i\in I},
-{(b'_j)}^{j\in J},v'.\, SV=\SV{{(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}} {v'} {e_b}
+\exists {(\alpha'_i)}^{i\in I},
+{(\beta'_j)}^{j\in J},v'.\, SV=\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} {v'} 
+{e_b}
 \\~~\land
-\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v' \land e_b
+\forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, \beta_j=\beta'_j \land v=v' 
+\land e_b
 \end{array} \bigg)\]
@@
     	{
-    	\{{b_{j}}\}^{j\in J_m}, \Pred_m, \Post_m}
+    	\{{\beta_{j}}\}^{j\in J_m}, \Pred_m, \Post_m}
     	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
@@
     	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
-    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in (I_1\uplus I_2)},b_j^{j\in J},v)\\ 
+    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in (I_1\uplus I_2)},\beta_j^{j\in J},v)\\ 
     		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
     	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
-    {\tt fresh}(\alpha_m,\alpha',b_j,v) 
+    {\tt fresh}(\alpha_m,\alpha',\beta_j,v) 
     }
@@
     		{
-    		\{{b_j}\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_1\uplus I_2} 
+    		\{{\beta_j}\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_1\uplus I_2} 
     		\Post_m}
@@
          {
-           \{{b_j}\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
+           \{{\beta_j}\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
          {s \OTarrow {v} s'}
@@
  \begin{mathpar}
-%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
+%    \left( fresh \ \overline{\alpha_i}, \overline{b_j}, v_x.\ \
     \inferrule*[myfraction=\reddottedrule]
          {
-           \{{b_{j x}}\}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+           \{{\beta_{j x}}\}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
          {t \OTarrow {v_x} t_x}
@@
 \hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-   \left( \forall j. b_j=b_{jx}  \Rightarrow \Pred_{OT_x}
+   \left( \forall j. \beta_j=\beta_{jx}  \Rightarrow \Pred_{OT_x}
      \land v\!=\!v_x \land  
@@
          {
-           \{{b_j}\}^{j\in J_1},\Pred,\Post}
+           \{{\beta_j}\}^{j\in J_1},\Pred,\Post}
          {s \OTWeakarrow {v} s'}
@@
          {
-           \{{b_{j x}}\}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+           \{{\beta_{j x}}\}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
          {t \OTWeakarrow {v_x} t_x}
@@
        	{
-       		\{{b_j}\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
+       		\{{\beta_j}\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
        	{s \OTarrow {v} {s}'}
@@
        	{
-       		\{{b_{j p x}}\}^{j\in J_{px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
+       		\{{\beta_{j p x}}\}^{j\in J_{px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
        	{t_p \OTarrow {v_{px}} t_{p x}}
@@
        	\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-       	\left( \forall j. b_j=b_{jpx}  \Rightarrow \Pred_{OT_{px}}
+       	\left( \forall j. \beta_j=\beta_{jpx}  \Rightarrow \Pred_{OT_{px}}
        	\land v\!=\!v_{px} \land
@@
        	{
-       		\{{b_{j p x y}}\}^{j\in J_{pxy}}, 
+       		\{{\beta_{j p x y}}\}^{j\in J_{pxy}}, 
        		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
@@
        	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
-       	\left( \forall j. b_{jpx}=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
+       	\left( \forall j. \beta_{jpx}=\beta_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
        	\land v_{px}\!=\!v_{pxy} \land
@@
        		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
-       		\left( \forall j. b_j=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
+       		\left( \forall j. \beta_j=\beta_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
        		\land v\!=\!v_{pxy} \land
@@
        		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-       		\left( \forall j. b_j=b_{jpx}  \Rightarrow \Pred_{OT_{px}}
+       		\left( \forall j. \beta_j=\beta_{jpx}  \Rightarrow \Pred_{OT_{px}}
        		\land v\!=\!v_{px} \land
@@
        		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-       		\left( \forall j. b_j=b_{jpx}  \Rightarrow (\Pred_{OT_{px}}\land\Pred_{p,u})
+       		\left( \forall j. \beta_j=\beta_{jpx}  \Rightarrow 
+       		(\Pred_{OT_{px}}\land\Pred_{p,u})
        		\land v\!=\!v_{px} \land
@@
        		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-       		\big( \forall j. b_j=b_{jpx}  \Rightarrow (\bigvee_{y\in Y} 
-       		\big( \forall j'. b_{j'px}=b_{j'pxy}  \Rightarrow \Pred_{OT_{pxy}}
+       		\big( \forall j. \beta_j=\beta_{jpx}  \Rightarrow (\bigvee_{y\in Y} 
+       		\big( \forall j'. \beta_{j'px}=\beta_{j'pxy}  \Rightarrow \Pred_{OT_{pxy}}
        		\land v_{px}\!=\!v_{pxy}\\\hspace{3em}~ \land
@@
        		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X} \bigvee_{y\in Y}
-       		\big( \forall j, j'. b_j=b_{jpx} \land b_{j'px}=b_{j'pxy}
+       		\big( \forall j, j'. \beta_j=\beta_{jpx} \land \beta_{j'px}=\beta_{j'pxy}
        		\Rightarrow \big( 
@@
  \bigvee_{x\in X} \bigvee_{y\in Y}
-\big( \forall j, j'. b_j=b_{jpx} \land b_{j'px}=b_{j'pxy}
+\big( \forall j, j'. \beta_j=\beta_{jpx} \land \beta_{j'px}=\beta_{j'pxy}
 \Rightarrow \big( 
@@
 \hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
-\left( \forall j. b_j=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
+\left( \forall j. \beta_j=\beta_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
 \land v\!=\!v_{pxy} \land
@@
 			{
-				\{{b_j}\}^{j\in J}, \Pred,  
+				\{{\beta_j}\}^{j\in J}, \Pred,  
 				\Post}
@@
 			{
-				\{{b_j}\}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
+				\{{\beta_j}\}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
 				\Pred\,',  
@@
 			{
-				\{\xrightarrow{b_j}\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
+				\{\xrightarrow{\beta_j}\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
 				\Post\,''}
@@
 		\end{mathpar}
-		and  $\Pred\subst{v_Q\leftarrow b_{j_0}} =(\Pred\,'
+		and  $\Pred\subst{v_Q\leftarrow \beta_{j_0}} =(\Pred\,'
 		\land \Pred\,'')$, $\Post=\Post\,'\uplus 
@@
 		{
-			\{{b_j}\}^{j\in J\cap\Holes(Q)}, \Pred_{j_0},  
+			\{{\beta_j}\}^{j\in J\cap\Holes(Q)}, \Pred_{j_0},  
 			\Post\,''}
@@
 $\Pred\,'=\bigwedge_{m\in I_k}\Pred_m  \land \Pred_{\symb{sv}}(SV_k,v_m^{m\in 
-I},b_j^{j\in J\cup \{j_0\}},v)$
-where\footnotemark[\thefootnote] $\Pred_{\symb{sv}}(SV_k,v_m^{m\in I},b_j^{j\in J\cup 
+I},\beta_j^{j\in J\cup \{j_0\}},v)$
+where\footnotemark[\thefootnote] $\Pred_{\symb{sv}}(SV_k,v_m^{m\in I},\beta_j^{j\in J\cup 
 \{j_0\}},v)\Leftrightarrow 
-\forall i\in I_k.\, \alpha_i=a_i\land \forall j \in J\cup \{j_0\}.\, \alpha_j=b_j \land 
+\forall i\in I_k.\, \alpha_i=a_i\land \forall j \in J\cup \{j_0\}.\, \alpha_j=\beta_j 
+\land 
 v=\alpha'
@@
 the source open transition except $\alpha_{j_0}=v_{j_0}$ has been replaced by  
-$\alpha_{j_0}=b_{j_0}$.
-Thus, $\Pred\subst{v_Q\leftarrow b_{j_0}}=(\Pred\,' 
+$\alpha_{j_0}=\beta_{j_0}$.
+Thus, $\Pred\subst{v_Q\leftarrow \beta_{j_0}}=(\Pred\,' 
 \land \Pred\,'')$. %\TODO{the argument on renaming has mostly been
@@
 	general, fresh variables appear in each transition inside
-        terms $b_j$, $v$, and 
+        terms $\beta_j$, $v$, and 
 	$\Pred$.}
@@
 actions of the holes, and the predicate involving $v_Q$ and the synchronisation vector is 
- more restrictive than the one involving only the variable $b_{j_0}$. This has no impact 
+ more restrictive than the one involving only the variable $\beta_{j_0}$. This has no 
+ impact 
  on the previous proof and this restriction  results from the composition of predicates.
@@
 	{
-		\{{b_j}\}^{j\in J}, 
+		\{{\beta_j}\}^{j\in J}, 
 		\Pred,  
@@
 	{
-		\{{b_j}\}^{j\in J_Q},
+		\{{\beta_j}\}^{j\in J_Q},
 		 \Pred\,',  
@@
 		{
-			\{{b_j}\}^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
-			\Pred\subst{b_{j_0}\leftarrow v_Q}\land\Pred\,',  
+			\{{\beta_j}\}^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
+			\Pred\subst{\beta_{j_0}\leftarrow v_Q}\land\Pred\,',  
 			\Post\uplus \Post\,'}
@@
 %    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m},
-%    	\{\xrightarrow{b_{j}}_j\}^{j\in J_m}, \Pred_m, \Post_m}
+%    	\{\xrightarrow{\beta_{j}}_j\}^{j\in J_m}, \Pred_m, \Post_m}
 %    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
@@
 transition is: $\Pred\,''=\bigwedge_{m\in I _1\uplus I_2}\Pred_m \land \Pred\,'
-\land \Pred(SV_k,a_i^{i\in I_k}\uplus(j_0\mapsto v_Q),b_j^{j\in J},v)$. By definition 
-$\Pred(SV_k,a_i^{i\in I}\uplus(j_0\mapsto v_Q),b_j^{j\in J},v)\Leftrightarrow
-	\forall i\in I.\, a_i=\alpha_i\land \forall j \in J.\, b_j=\alpha_j \land 
+\land \Pred(SV_k,a_i^{i\in I_k}\uplus(j_0\mapsto v_Q),\beta_j^{j\in J},v)$. By definition 
+$\Pred(SV_k,a_i^{i\in I}\uplus(j_0\mapsto v_Q),\beta_j^{j\in J},v)\Leftrightarrow
+	\forall i\in I.\, a_i=\alpha_i\land \forall j \in J.\, \beta_j=\alpha_j \land 
 	\alpha'_k=v\land v_Q=\alpha_{j_0}\land e_b$, finally 
-	$\Pred\,''=\Pred\subst{b_{j_0}\leftarrow 
+	$\Pred\,''=\Pred\subst{\beta_{j_0}\leftarrow 
 	v_Q} \land \Pred\,'$. The post-condition gathers the post-conditions related to all 
@@
  {
- 	\{{b_j}\}^{j\in J},\Pred_{OT},\Post_{OT}}
+ 	\{{\beta_j}\}^{j\in J},\Pred_{OT},\Post_{OT}}
  { \ostate{s_{i}^{i \in L_P\uplus L}}\OTarrow {v} \ostate{{s'}_{i}^{~i \in 
@@
  	{
- 		\{{b_j}\}^{j\in J'}, 
+ 		\{{\beta_j}\}^{j\in J'}, 
  		\Pred\,',  
@@
  	{
- 		\{\xrightarrow{b_j}\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
+ 		\{\xrightarrow{\beta_j}\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
  		\Post\,''}
@@
  }\end{mathpar}
- and  $\Pred_{OT}\subst{v_Q\leftarrow b_{j_0}} =({\Pred\,'}
+ and  $\Pred_{OT}\subst{v_Q\leftarrow \beta_{j_0}} =({\Pred\,'}
  \land {\Pred\,}'')$, $\Post_{OT}=\Post\,'\uplus 
@@
  {
- 	\{\xrightarrow{b_{j x}}\}^{j\in J\cap\Holes(Q)}, 
+ 	\{\beta_{j x}\}^{j\in J\cap\Holes(Q)}, 
  	\Pred_{OT_x},\Post_{OT_x}}
@@
  \Rightarrow \bigvee_{x\in X}
- \left( \forall j\in J\cap \Holes(Q). b_j=b_{jx}  \Rightarrow 
+ \left( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \Rightarrow 
  \Pred_{OT_x}
@@
  $i\in L_P$, $t_{i}=s_{i}$ and $t_{i x}=s'_{i}$, and for $j\in Holes(P)$, 
- $b_{j x}=b_j$):\\[-2ex]
+ $\beta_{j x}=\beta_j$):\\[-2ex]
  \[ P[Q']_{j_0}  
@@
  	{
- 		\{{b_{j x}}\}^{j\in J}, 
- 		\Pred\,'\subst{b_{j_0 x}\leftarrow v_x}\land\Pred_{OT_x},  
+ 		\{{\beta_{j x}}\}^{j\in J}, 
+ 		\Pred\,'\subst{\beta_{j_0 x}\leftarrow v_x}\land\Pred_{OT_x},  
  		\Post\,'\uplus \Post_{OT_x} }
@@
  \begin{small} $\Pred_{s,t} \land \Pred_{OT} \implies
- 	\Pred_{s,t}\land(\Pred\,'\land \Pred\,'')\subst{b_{j_0}\leftarrow v_Q}\\ % reversed 
+ 	\Pred_{s,t}\land(\Pred\,'\land \Pred\,'')\subst{\beta_{j_0}\leftarrow v_Q}\\ % 
+ 	%reversed 
  	%substitution 
  	\implies 
- 	(\Pred_{s,t}\land\Pred\,'')\land \Pred\,'\subst{b_{j_0}\leftarrow v_Q}\\ % $b_{j_0}$ 
+ 	(\Pred_{s,t}\land\Pred\,'')\land \Pred\,'\subst{\beta_{j_0}\leftarrow v_Q}\\ % 
+ 	%$b_{j_0}$ 
  	%only 
@@
  	{\displaystyle\bigvee_{x\in X}
- 	\left( \forall j\in J\cap \Holes(Q). b_j=b_{jx}  \Rightarrow 
+ 	\left( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \Rightarrow 
  	\Pred_{OT_x}
@@
  }
- \\~\qquad\qquad	\land \Pred\,'\subst{b_{j_0}\leftarrow v_Q} \\
+ \\~\qquad\qquad	\land \Pred\,'\subst{\beta_{j_0}\leftarrow v_Q} \\
  	\implies
@@
  	{\displaystyle\bigvee_{x\in X}
- 		\left( \forall j\in J\cap \Holes(Q). b_j=b_{jx}  \Rightarrow 
- 		\Pred\,'\subst{b_{j_0}\leftarrow v_x}\land \Pred_{OT_x}
+ 		\left( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \Rightarrow 
+ 		\Pred\,'\subst{\beta_{j_0}\leftarrow v_x}\land \Pred_{OT_x}
  		\land v_Q\!=\!v_x \land  
@@
  restricted the 
- substitution as $b_{j_0}$ only appears in $\Pred\,'$; then we
+ substitution as $\beta_{j_0}$ only appears in $\Pred\,'$; then we
  applied the property of FH-bisimulation for $P$ and rearranged the
@@
 	{
-		\{{b_j}\}^{j\in J},\Pred_{OT},\Post_{OT}}
+		\{{\beta_j}\}^{j\in J},\Pred_{OT},\Post_{OT}}
 	{ \ostate{s_{i}^{i \in L\uplus L_Q}}\OTarrow {v} \ostate{{s'}_{i}^{~i \in 
@@
 				{
-					\{{b_j}\}^{j\in J'}, 
+					\{{\beta_j}\}^{j\in J'}, 
 					\Pred\,',  
@@
 				{
-					\{{b_j}\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
+					\{{\beta_j}\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
 					\Post\,''}
@@
 			}\end{mathpar}
-			and  $\Pred_{OT}\subst{v_Q\leftarrow b_{j_0}} =({\Pred\,}'
+			and  $\Pred_{OT}\subst{v_Q\leftarrow \beta_{j_0}} =({\Pred\,}'
 			\land {\Pred\,}'')$, $\Post_{OT}=\Post\,'\uplus 
@@
 			{
-				\{{b_{j x}}\}^{j\in J'}, 
+				\{{\beta_{j x}}\}^{j\in J'}, 
 				\Pred_{OT_x},\Post_{OT_x}}

### 2018-03-27 2018-Arch-pNets/arch-pNets.tex
alphas and betas
notations in weak + ref a forte

@@
 \begin{definition}[pNets]\label{def-pnets}
-A pNet is a hierarchical structure where leaves are pLTSs and holes:\\\noteSB{I would not put a new line here}
+A pNet is a hierarchical structure where leaves are pLTSs and holes\footnote{Typing can 
+be added to pNets by defining and checking their interfaces, called 
+sort~\cite{HMZ-FORTE2016}}:
 $\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, J, \symb{SV}_k^{k\in 
@@
 
-	\begin{description}
-		\item[{\bf Tr2:}]\noteSB{I do not understand why the second line $pNet_m \models\dots$ is not subsumed by the first one?}
-	\end{description}
-
-	\noindent
-    $\inferrule
-    {k\!\in\! K \\SV_k \!=\! \alpha_m^{m \in I\uplus J} \!\to\! 
-    \alpha' |g \\
-    	Leaves(\mylangle \pNet_i^{i\in I'}, \overline{\Sort}, \symb{SV}_k^{k\in 
-    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \\    	
-    	\forall m\!\!\in\!\! I. 	
-    {\left(\begin{array}{l}
-	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
-    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
-    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
-    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
-    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
-		{ \pNet_m 
-    	 \models
-    	\inferrule*[myfraction=\reddottedrule]
-    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
-    	{\ostate{s_m} \OTarrow {v_m}
-    		\ostate{s_m'}} \land I'_m=\{m\} \land J'_m=\emptyset}
-\end{array}\right)}\\
-    	%\land
-    	%Leaves(\pNet_m) = \overline{\pLTS}^{L_k})  	
-     J' = \biguplus_{m\in I}\!\! J'_m \uplus J 	\\
-    	\Pred = \bigwedge_{m\in I}\!\! \Pred_m \land
-    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in I},b_j^{j\in J},v)\\ 
-    		I' = \biguplus_{m\in I}\!\! I_m'
-    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
-    {\tt fresh}(\alpha_m,\alpha',b_j,v) 
-    }
-    {\mylangle \pNet_i^{i\in I'}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
-    	\models
-    	{\inferrule*[myfraction=\reddottedrule]
-    		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I^\prime},
-    		\{\xrightarrow{b_j}_j\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_k} 
-    		\Post_m}
-    		{\ostate{s_i^{i\in L}} \OTarrow {v}
-    			\ostate{(s_i^\prime)^{i\in L}}}
-    	}
-    }
-    $
+%OLD	\begin{description}
+%		\item[{\bf Tr2:}]\noteSB{I do not understand why the second line $pNet_m 
+%\models\dots$ is not subsumed by the first one?}
+%	\end{description}
+%	
+%	\noindent
+%    $\inferrule
+%    {k\!\in\! K \\SV_k \!=\! \alpha_m^{m \in I\uplus J} \!\to\! 
+%    \alpha' |g \\
+%    	Leaves(\mylangle \pNet_i^{i\in I'}, \overline{\Sort}, \symb{SV}_k^{k\in 
+%    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \\    	
+%    	\forall m\!\!\in\!\! I. 	
+%    {\left(\begin{array}{l}
+%	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
+%    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
+%    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
+%    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
+%    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
+%		{ \pNet_m 
+%    	 \models
+%    	\inferrule*[myfraction=\reddottedrule]
+%    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
+%    	{\ostate{s_m} \OTarrow {v_m}
+%    		\ostate{s_m'}} \land I'_m=\{m\} \land J'_m=\emptyset}
+%\end{array}\right)}\\
+%    	%\land
+%    	%Leaves(\pNet_m) = \overline{\pLTS}^{L_k})  	
+%     J' = \biguplus_{m\in I}\!\! J'_m \uplus J 	\\
+%    	\Pred = \bigwedge_{m\in I}\!\! \Pred_m \land
+%    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in I},b_j^{j\in J},v)\\ 
+%    		I' = \biguplus_{m\in I}\!\! I_m'
+%    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
+%    {\tt fresh}(\alpha_m,\alpha',b_j,v) 
+%    }
+%    {\mylangle \pNet_i^{i\in I'}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
+%    	\models
+%    	{\inferrule*[myfraction=\reddottedrule]
+%    		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I^\prime},
+%    		\{\xrightarrow{b_j}_j\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_k} 
+%    		\Post_m}
+%    		{\ostate{s_i^{i\in L}} \OTarrow {v}
+%    			\ostate{(s_i^\prime)^{i\in L}}}
+%    	}
+%    }
+%    $
 	\medskip

### 2018-03-28 2016-Weak-FH-Bisim/WeakBisim.tex
notations in weak + ref a forte
coorection and explanations of Fig3/example1

--- 2018-03-27 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 argument, through the two protocol entities $sender$ and
-$receiver$. The underlying unsafe network is modelled by two media,
+$receiver$. The underlying network is modelled by two media,
 carrying the message together with a control bit on one way, and an
@@
 
-\TODO{Add somewhere a subsection ``running example'' ?}
+%\TODO{Add somewhere a subsection ``running example'' ?}
 
@@
   \label{OT:ABP}
-  The \texttt{Protocol} pNet of Fig. \ref{schema:ABP-composed} has 4 controllers and no holes. One of its possible open-transition (the sender sending $m,b$ to the medium) is:
+  The \texttt{Protocol} pNet of Fig. \ref{schema:ABP-composed} has 4 controllers and no holes. One of its possible open-transition (the sender sending $(m,b)$ to the medium) is:
 
@@
 
-At the upper level, the $ABP$ pNet has 2 holes and and $Protocol$ has a subnet. One of its possible transition (synchronizing the hole $P$ with the $Protocol$) is:
+    \smallskip
+    Here the global states $Prot_1$ and $Prot_2$ encode the states of
+    the 4 pLTS composing the system, namely
+    $Prot_1=\ostate{s_1,m_0,m_0,r_0}$ and
+    $Prot_2=\ostate{s_2,m_1,m_0,r_0}$, showing that the sender and the
+    first medium have evolved during this transition.
+    The predicate $Pred$ involves the state variables $s_1\_m$ and
+    $s_1\_sb$ of the sender, while the assignment $Post$ sets the
+    state variables of the medium.
+
+    \smallskip
+At the upper level, the $ABP$ pNet has 2 holes and and $Protocol$ has
+a subnet. One of its possible transition (synchronizing the hole $P$
+with the $Protocol$) is:
+
  \smallskip
@@
     $
+
+    \smallskip
+    The global states $ABP_1$ and $ABP_2$ have the same structure than
+    $Prot_1$ and $Prot_2$, as the holes have no states. The assignment
+    $Post$ uses a variable from the action of hole $P$ to set the
+    value of the sender state variable $s1\_m$.
 \end{example}

### 2018-03-28 2016-Weak-FH-Bisim/WeakBisim.tex

--- 2018-03-27 2016-Weak-FH-Bisim/WeakBisim.tex
@@
        Definition~\ref{def:operationalSemantics}.
-	\begin{description}
-		\item[{\bf Tr2:}]
-	\end{description}
+
+\noindent\textbf{Tr2:}\\
 	\noindent
-    $\inferrule
+\begin{mathpar}
+    \mprset {vskip=1ex}
+\inferrule
     {
-	\forall m\!\!\in\!\! I_1. {\pNet_m \models\mprset{myfraction=\reddottedrule}\inferrule
+\Leaves(\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in 
+    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
+k\!\in\! K \qquad SV_k \!=\! \SV{\alpha_m^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} \\
+\\     	
+	\forall m\!\!\in\!\! I_1. {\pNet_m 
+	\models\mprset{myfraction=\reddottedrule}\inferrule
     	{
@@
     }
-    $
-	\medskip
+\end{mathpar}
 
@@
 			\{{\beta_j}\}^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
-			\Pred\subst{\beta_{j_0}\leftarrow v_Q}\land\Pred\,',  
+			\Pred\land\Pred\,'\subst{\beta_{j_0}\leftarrow v_Q},  
 			\Post\uplus \Post\,'}
@@
 transition is: $\Pred\,''=\bigwedge_{m\in I _1\uplus I_2}\Pred_m \land \Pred\,'
-\land \Pred(SV_k,a_i^{i\in I_k}\uplus(j_0\mapsto v_Q),\beta_j^{j\in J},v)$. By definition 
+\land \Pred(SV_k,v_i^{i\in I_1\uplus I_2}\uplus(j_0\mapsto v_Q),\beta_j^{j\in J},v)$. By 
+definition 
 $\Pred(SV_k,a_i^{i\in I}\uplus(j_0\mapsto v_Q),\beta_j^{j\in J},v)\Leftrightarrow

### 2018-03-28 2016-Weak-FH-Bisim/WeakBisim.tex
comments on lemma 2

--- 2018-03-27 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 \newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
-\newcommand{\LUDO}[1]{\textcolor{green}{#1}}
+\definecolor{darkgreen}{rgb}{0.1, 0.5, 0.1}
+\newcommand{\LUDO}[1]{\textcolor{darkgreen}{#1}}
 \newcommand{\RAB}[1]{\textcolor{magenta}{#1}}
@@
 \end{lemma}
+\TODO{important comment added:}
+Note that this does not mean that any two pNets can be composed and produce an open 
+transition. Indeed, the predicate $\Pred\,'\subst{\beta_{j_0}\leftarrow v_Q}$ might not 
+be satisfiable if the open transition of $Q$ cannot be matched with $\beta_{j_0}$.
+
+\LUDO{Question/comment: this formulation makes the proof easy and supposes that we use 
+enough 
+variables, which is in accordance with the implementation and the way we define SV, but I 
+believe that $\Pred\,'\land \beta_{j_0}= v_Q$ might be better because more flexible and 
+less dependant of the way OTs are defined}
+
 \begin{small}

### 2018-03-28 2016-Weak-FH-Bisim/WeakBisim.tex
algo, elim, WOT

--- 2018-03-28 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
-\TODO{Eric: refine the algorithm description}
+\TODO{Eric: refine the algorithm description - \ERIC{Done, can you check ?}}
 
@@
 
-2) While there are unexplored states:
-
-2a) pick one state from the unexplored set and add it to the explored
-set. From this state
+2) While there are unexplored states, pick one state from the
+unexplored set and add it to the explored set.
+
+2a- From this state
 build all possible deduction trees by application of the structural
-rules Tr1 and Tr2, using all \ERIC{applicable} combinations
+rules Tr1 and Tr2, using all applicable combinations
 of synchronisation vectors.
-
-2b) For each of the obtained deduction trees:\\
-- Extract the resulting open-transition, with its predicate and
-\Post\ assignments by exploring the structure of the pNet.
-
-- The predicate is submitted to Z3 for checking satisfiability. If it
-is NOT stisfiable, the resulting OT is discarded. This will minimize
-the number of resulting transitions, and potentialy prune the search-space.
-
-- For each open-transition,  add the transition in the outgoing transitions of
-the current state, and add the
+In practice, the algorithm does not explicitely construct the
+deduction tree, but for each pNet node, builds all possible
+combinations of the OTs of its subnets, and filter these combinations
+by matching with all synchronisation vectors.
+
+2b- For each OT built, add the transition in the
+outgoing transitions of the current state, and add the
 resulting state in the unexplored set if it is not already there.
 
-%3) this ends with the "while" from step 2, when we have no more
-%unexplored set.
+3) The predicate is submitted to Z3 for checking satisfiability. If it
+is NOT satisfiable, the resulting OT is discarded. This will minimize
+the number of resulting transitions, and by reachability analysis,
+reduce the resulting open automaton.
+
 \end{algorithm}
@@
 holes, and each pLTS at leaves having a finite number of states and
-(symbolic) transitions, has a finite automaton (see \ref{Forte}).
+(symbolic) transitions, has a finite automaton (see \ref{henrio:Forte2016}).
 
@@
 
-\ERIC{Optionally, simplify the predicate by eliminating the unnecessary intermediate variables, that were produced as fresh local variables of synchronisation vectors, and fresh result variables of intermediate OTs.
+While building the open transitions, many new variable names are
+created, as fresh local variables of synchronisation vectors, and
+fresh result variables of intermediate OTs. While these are required
+for the semantic construction, they are not significant in the
+resulting open automaton. In fact they carry information on the
+internal structure of the pNet system, and this information should
+\_not\_ be visible when looking at the system as a black box, and in
+particular when comparing its behaviour with another system, e.g. by
+bisimulation.
+
 In the resulting predicate the only significant variables are :\\
-- the input variables of pLTS transitions\\
+- the input variables of pLTS transitions \TODO{heu, non, meme pas, si
+  ce sont des comm internes!}\\
 - the actions of holes\\
-- the result action at toplevel.}
-
-  \TODO{Eric: define ``elimination of intermediate variables ?'' it
-    transforms the predicates, it is not an
-    ``equivalence'' transformation, rather some sort of
-    abstraction... Does it change the satisfiability ?}
-
-%% \begin{theorem}[Finiteness of open-automata.]\\
-%% Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
-%%   J}$, if the sets $L$ and $J$ are finite, if the synchronisation vectors of all pNets 
-%%   included in  $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ 
-%%   are finite, and if
-%% $\forall i \in L.\, finite{(states(pLTS_i))} \text{ and } pLTS_i$
-%% has a finite number of state variables, then Algorithm 1 terminates
-%% and produces an open automaton 
-%% $\mathcal{T}$ with finitely many states and transitions.
-
-% Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in
-%     K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
-%   J}$,
-% build its semantics as in algorithm 1.
-
-% We have:
-
-% $$ finite{(L)} \land finite{(J)} \land \forall i \in L finite{(\{s_i\})}
-%   \to finite{(\mathcal{T})}$$
-% \end{theorem}
-
-\TODO{Eric: full result of the tool execution on the running example}
+- the result action at toplevel.
+
+So we transform the predicates of the resulting OTs, eliminating all
+intermediate variables. \TODO{Explain why this should work !! Maybe
+  need to be more precise on unification in the matching...}
+
+\TODO{Eric: full (???) result of the tool execution on the running example}
 
@@
 The ``saturation'' step in the construction of the weak relation will
-pick all $\tau^*$ and $\tau^*;a$ sequences from the OA, and build a weak
+pick all $\tau^*$ and $\tau^*;a;\tau^*$ sequences from the OA, and build a weak
 OT from each sequence. Here is one example:
@@
     m=s_1\_m]}\ostate{2100}$\\
-$\qquad\ostate{2100}$ variables: $\psi_1 = \{m_1\_m:=m; m_1\_x:=x; s_2\_b:=s_1\_b\}$;\\
+and $\qquad\ostate{2100}$ variable assignments are: $\psi_1 = \{m_1\_m:=m; m_1\_x:=x; s_2\_b:=s_1\_b\}$;\\
 \\
@@
   \phi_2 = [r_0\_b=b \land m'=m_1\_m \land b=m_1\_x]}\ostate{2001}$\\
-$\qquad\ostate{2001}$ variables: $\psi_2 = \{r_1\_b:=r_0\_b; r_1\_m:=m;
+and $\qquad\ostate{2001}$ assignments: $\psi_2 = \{r_1\_b:=r_0\_b; r_1\_m:=m;
 ; s_2\_b:=s_1\_b\}$;\\
@@
   \phi_3 = [v=out(r_1\_m)]}\ostate{2002}$\\
-$\qquad\ostate{2002}$ variables: $\psi_3 = \{r_2\_b:=r_1\_b; s_2\_b:=s_1\_b\}$;\\
-
-Resulting Weak Transition:
-
-\noindent
-$\ostate{1000}\OTWeakarrow{v,
-  \phi = \phi_1\land\phi_2\psi_1\land\phi_3\psi_2\psi_1}\ostate{2002}$\\
-\\
-$\phi=[x=s_1\_b \land m=s_1\_m\\
-  \land r_0\_b=b \land m'=m_1\_m \land b=m_1\_x\\
-  \land v=out(r_1\_m)]\\
-and \\
-\psi= \{r_2\_b:=r_0\_b\}$
-
-Note that in $\phi$ the application of assignments
+and $\qquad\ostate{2002}$ variablesassignments: $\psi_3 = \{r_2\_b:=r_1\_b; s_2\_b:=s_1\_b\}$;\\
+
+The resulting Weak Transition has a predicate $\phi =
+\phi_1\land\phi_2\psi_1\land\phi_3\psi_2\psi_1 = \phi=[x=s_1\_b \land m=s_1\_m
+  \land r_0\_b=b \land m'=m_1\_m \land b=m_1\_x
+  \land v=out(r_1\_m)]$
+and assignment
+$\psi= \{r_2\_b:=r_0\_b\}$.
+
+We can see here that in $\phi$ the application of assignments
 $\psi_1,\psi_2,\psi_3$ have already ``eliminated'' the intermediate
 state variables
-$m_1\_m, b=m_1\_x, r_1\_m$, but not the intermediate input variables
+$m_1\_m, b=m_1\_x, r_1\_m$, and not the intermediate input variables
 $m,m',x,b$. But now $\phi$ includes enough information to eliminate them, giving
-a final $\phi'= [v=out(s_1\_m)\land r_0\_b=s_1\_b]$
+a final $\phi'= [v=out(s_1\_m)\land r_0\_b=s_1\_b]$, so the resulting
+WOT is:
+
+ \noindent
+ $$\ostate{1000}\OTWeakarrow{v,
+   [v=out(s_1\_m)\land r_0\_b=s_1\_b],\{r_2\_b:=r_0\_b\}} \ostate{2002}$$
+%% \\
+%% $\phi=[x=s_1\_b \land m=s_1\_m\\
+%%   \land r_0\_b=b \land m'=m_1\_m \land b=m_1\_x\\
+%%   \land v=out(r_1\_m)]\\
+%% and \\
+%% \psi= \{r_2\_b:=r_0\_b\}$
+
+%% Note that
 

### 2018-04-05 2018-Arch-pNets/arch-pNets.tex
clarifications -- 2 comments treated

@@
 A pNet has a set of sub-pNets that can be either pNets or pLTSs, and a
-set of \replaceSB{Holes}{holes}, playing the role of process parameters.
+set of holes, playing the role of process parameters.
 
@@
 Actions involved at the pNet level (in the synchronisation vectors) do
-not \replaceSB{need to distinguish  input 
-variables. Action terms for pNets are defined as follows:}{have input variables, \ie they 
-have the form $a(\Expr_j^{j \in J})$.}
-\removeSBin{
-%\[
-%\begin{array}[l]{rcl@{\quad}l}
-$  \alpha\in \AlgAS ::=a(\Expr_1,\ldots,\Expr_n)$
-%\end{array}
-%\]
-}
+not have input variables, \ie they 
+have the form $a(\Expr_j^{j \in J})$.
 
@@
 The semantics of open pNets will be defined  as an open automaton. An open
-automaton is an automaton where \noteSB{This might give a false impression that there is some kind of CCS-like ``duality'' between pLTSs and holes}\hl{each transition composes transitions of several LTSs with
-actions of some holes}, the transition occurs if some predicates hold, and can involve a 
+automaton is an automaton where each transition composes the actions of several holes, 
+the transition occurs if some predicates hold, and can involve a 
 set of state modifications.

### 2018-04-06 2018-Arch-pNets/arch-pNets.tex
Updated the proofs to include maximal progress Had to introduce the notion of upwards compatibility

--- 2018-03-27 2018-Arch-pNets/arch-pNets.tex
@@
 \newcommand{\secn}[1]{Sect.~\ref{secn:#1}}
-\newcommand{\rem}[1]{Rem.~\ref{rem:#1}}
+\newcommand{\rem}[1]{Note~\ref{rem:#1}}
 \newcommand{\lem}[1]{Lem.~\ref{lem:#1}}
@@
   \[q \goesto{a, g, e} q'\,.\]
-  In fact, I even use capital letters: in the definition of
-  interaction model composition, I use
-  \[\cdot \goesto{a, G, E} \cdot\]
-  in the conclusion of the rule.  However, for this latter I can
-  easily change the notation.
+  %% In fact, I even use capital letters: in the definition of
+  %% interaction model composition, I use
+  %% \[\cdot \goesto{a, G, E} \cdot\]
+  %% in the conclusion of the rule.  However, for this latter I can
+  %% easily change the notation.
 
@@
     \\[6pt]
-    \val{\#2}{\#3} &
-    {\ttfamily\textbackslash val\{\#2\}\{\#3\}} &
+    \val[]{\#2}{\#3} &
+    {\ttfamily\textbackslash val[]\{\#2\}\{\#3\}} &
     {\ttfamily\#1\{\textbackslash sigma\}\^{}\{\#2\}\_\{\#3\}}
@@
 %
-  Notations $q \goesto{a} q'$ and $q \goesto{a}$ are as usual;
+  Notations $q \goesto{a, g, e} q'$ and $q \goesto{a, g, e}$ are as usual;
   for a component $B$, we denote $Q_B$, $q^0_B$, $V_B$, $\val{0}{B}$, $P_B$,
@@
 
-  We denote $\filter{\alpha} \bydef{=} \setdefb{\beta \in (2^P \times
+  We write $\alpha \prec_\pi \beta$ for $(\alpha, \beta) \in \pi$ and 
+  denote $\filter{\alpha} \bydef{=} \setdefb{\beta \in (2^P \times
     \guards{V} \times \exprs{V})}{\alpha \prec_\pi \beta}$ the set of
@@
     }{
-      q \goesto{a, g', e} q'
+      q \goesto[\pi]{a, g', e} q'
     }\,, 
@@
 \begin{note}
-  Below, we will assume that the maximal progress priority is
+  \label{rem:maxprogress}
+  Below, we will assume that the maximal progress priority $\mu$ is
   applied after each composition with an interaction model.
@@
 %
+  $\IMextend{\Gamma}{P}$ is the \emph{extension} of the interaction
+  model $\Gamma$ to the set of ports $P$, \ie the interaction model
+  over $(V, P, \export)$, with
+  \[
+  \export(p) = 
+  \begin{cases}
+    \export[C](p), & \text{for all } C \in \cC, p \in P_C,
+    \\
+    \export[B](p), & \text{for all } B \in \cB, p \in P_B,
+  \end{cases}
+  \]
+  defined by
+%
   \begin{equation}
@@
     }
+    ;
   \end{equation}
 %
-  denotes the \emph{extension} of the interaction model $\Gamma$
-  to the set of ports $P$
-  and $\mu$ is the maximal progress priority model.
+  $\mu$ is the maximal progress priority model.
 \end{definition}
@@
     \Gamma = \setdefb{
-      (a, g_1 \land g_2, e_1 \expmix e_2) 
+      (a, g^1 \land g^2, e^1 \expmix e^2) 
     }{
-      (a \cap P_{A_i}, g_i, e_i) \in \Gamma_i,
+      (a \cap P_{A_i}, g^i, e^i) \in \Gamma_i,
       \text{ for } i = 1,2
@@
   are deterministic; $A_{id} = \bigl(\emptyset, \emptyset,
-  \emptyset, \{\emptyset\}\bigr)$ is its neutral element, \ie for
+  \emptyset, \emptyset, \{(\emptyset, \true, \noop)\}\bigr)$ is its neutral element, \ie for
   any architecture $A$, we have $A \oplus A_{id} \arequiv A$.
-  Furthermore, for any component $B$, we have $A_{id}(B) = B$.
+  Furthermore, for any component $B$, we have $A_{id}(B) = \mu(B)$.
 \end{proposition}
@@
 \end{proof}
+
+The last statement of \prop{arcomp:nice} highlights a subtle point:
+$A_{id}$ is the neutral element of the $\arcomp$ operator\mdash it is
+not the identity operator on components.
 
@@
 
+\begin{definition}[Upwards compatibility]
+  \label{defn:up:compat}
+  \todoSB{Summarise in English and move to the appendix}
+%
+  Consider two architectures $A_i = (\cC_i, V_{A_i}, P_{A_i},
+  \export[A_i], \Gamma_i)$, for $i = 1,2$.
+%
+  We say that $A_1$ and $A_2$ are \emph{upwards compatible} iff, for
+  any two interactions $(a_i, g_i, e_i) \in \Gamma_i$, such that $a_1
+  \cap P_{A_2} = a_2 \cap P_{A_1}$ (\ie they agree on the common ports
+  of the two architectures), we have 1)~for any interaction $(b_1,
+  h_1, f_1) \in \Gamma_1$, such that $a_1 \varsubsetneq b_1$, there
+  exists an interaction $(b_2, h_2, f_2) \in \Gamma_2$, such that $a_2
+  \subseteq b_2$, $b_1 \cap P_{A_2} = b_2 \cap P_{A_1}$ and the 
+  implication  
+%
+  \begin{multline*}
+    \left(
+    \exists (q^1_C)^{C \in \supp{b_1} \cap \cC_1}:
+    \exists (q^2_C)^{C \in \supp{a_2} \cap \cC_2}:
+    \bigwedge_{
+      \begin{multlined}
+        \scriptstyle
+        C \in \supp{b_1} \cap \cC_1 \cap
+        \\
+        \scriptstyle
+        \supp{a_2} \cap \cC_2
+      \end{multlined}
+    }
+    q^1_C = q^2_C
+    \ \land
+    \right.
+    \\
+    \begin{aligned}
+      \exists \bigl(q^1_C \goesto{b_1 \cap P_C, g^{b_1}_C, e^{b_1}_C}\bigr)^{C \in \supp{b_1} \cap \cC_1}:
+      & \quad \left.
+      h_1 \land \bigwedge_{C \in \supp{b_1} \cap \cC_1} g^{b_1}_C
+      \ \land \right.
+      \\
+      \exists \bigl(q^1_C \goesto{a_1 \cap P_C, g^{a_1}_C, e^{b_1}_C}\bigr)^{C \in \supp{a_1} \cap \cC_1}:
+      & \quad \left.
+      g_1 \land \bigwedge_{C \in \supp{a_1} \cap \cC_1} g^{a_1}_C
+      \ \land \right.
+      \\
+      \exists \bigl(q^2_C \goesto{a_2 \cap P_C, g^{a_2}_C, e^{a_2}_C}\bigr)^{C \in \supp{a_2} \cap \cC_2}:
+      & \quad
+      \left.
+      g_2 \land \bigwedge_{C \in \supp{a_2} \cap \cC_2} g^{a_2}_C
+      \right) \implies 
+    \end{aligned}
+  \end{multline*}
+%
+  \begin{multline*}
+    \left(
+    \exists (q^2_C)^{C \in (\supp{b_2}\setminus\supp{a_2}) \cap \cC_2}:
+            {\color{white}\bigwedge_{C \in \cC_1}}\right. % Fake bigwedge to make the parenthesis the right size
+            \\
+            \left.
+            \exists \bigl(q^2_C \goesto{b_2 \cap P_C, g^{b_2}_C, e^{b_2}_C}\bigr)^{C \in \supp{b_2} \cap \cC_2}:
+            h_2 \land
+            \bigwedge_{C \in \supp{b_2} \cap \cC_2} g^{b_2}_C
+            \right)
+  \end{multline*}
+%  
+  holds for all valuations $\val{}{1} : V_{A_1} \rightarrow \data$
+  and $\val{}{2} : V_{A_2} \rightarrow \data$; and 2)~symmetrically
+  for any interaction $(b_2, h_2, f_2) \in \Gamma_2$, such that $a_2
+  \varsubsetneq b_2$.
+\end{definition}
+
 \begin{theorem}[Preserving enforced properties]
@@
   Let $\cB$ be a set of components; let $A_i = (\cC_i, V_{A_i},
-  P_{A_i}, \export[A_i], \Gamma_i)$, for $i = 1,2$, be two architectures
+  P_{A_i}, \export[A_i], \Gamma_i)$, for $i = 1,2$, be two upwards compatible architectures
   enforcing on $\cB$ the properties $\Phi_1$ and $\Phi_2$
@@
   \label{lem:onlyone}
-  Let $A = (\cC, V_A, P_A, \Gamma)$ be an architecture and denote
+  Let $A = (\cC, V_A, P_A, \export[A], \Gamma)$ be an architecture and denote
   by $\Gamma_\cC \bydef{=}
@@
   the projection of $\Gamma$ onto the coordinating components of
-  $A$.  Consider the architecture $A' = (\{C'\}, V_A, P_A,
+  $A$.  Consider the architecture $A' = (\{C'\}, V_A, P_A, \export[A],
   \Gamma)$, where $C' = \Gamma_\cC(\cC)$.  For any set of
@@
 \begin{proof}
-  First of all, notice that, by \defn{im},
-  $V_{C'} = \bigcup_{C \in \cC} V_C$ and $P_{C'} = P_\cC$.
+  First of all, notice that, by \defn{im:sem},
+  $V_{C'} = \bigcup_{C \in \cC} V_C$ and $P_{C'} = P_\cC = \bigcup_{C \in \cC} P_C$.
   The conditions of \defn{arch} are satisfied and $A'$ is indeed
@@
 
-  Clearly the state spaces, initial states and interfaces of both
-  components coincide.  Thus we only have to prove that so do the
+  Clearly the state spaces and initial states %% and interfaces
+  of both LTSs $\semopen{A(\cB)}$ and $\semopen{A'(\cB)}$
+  coincide.  Thus, we only have to prove that so do the
   transition relations.  Let us assume that
@@
 
-  By \defn{comp:semantics}, a transition
+  By \defn{comp:semantics},
 %
@@
     q_i^{i \in I} q_j^{j \in J}
-    \goesto{a, G, E}
+    \goesto{a, g', e'}
     (q_i')^{i \in I} (q_j')^{j \in J}
@@
     \val{i \in I}{i} \val{j \in J}{j}
-    \models G
+    \models g'
     \,,
@@
     (\val{\prime}{i})^{i \in I} (\val{\prime}{j})^{j \in J}
-    = \val[\tilde]{}{}[E]
+    = \val[\tilde]{}{}[e']
     \,,
@@
       \val[\tilde]{}{}} \subseteq \export(a)       
-    \,.   
   \end{mathpar}
-
-  By \defn{im}, \eq{lem1:trans} is a transition in $A(\cB)$
+%
+  (with $\export$ defined as in \defn{arch:application}).
+
+  By \defn{im:sem} and \defn{priority:sem}, \eq{lem1:trans} is a transition in $A(\cB)$
   iff $a \neq \emptyset$, $(a, g, e) \in \IMextend{\Gamma}{P}$,
@@
   \begin{enumerate}
-  \item for $i \in I$,
-    $q_i \goesto{a \cap P_{C_i}, g_{C_i}, e_{C_i}} q_i'$
-    is a transition in $C_i$, or
-    $a \cap P_{C_i} = \emptyset$ and $q_i = q_i'$,
-    $g_{C_i} = \true$ and $e_{C_i} = \noop$\,;
-  \item for $j \in J$,
-    $q_j \goesto{a \cap P_{B_j}, g_{B_j}, e_{B_j}} q_j'$
-    is a transition in $B_j$, or
-    $a \cap P_{B_j} = \emptyset$ and $q_j = q_j'$,
-    $g_{B_j} = \true$ and $e_{B_j} = \noop$\,;
-  \item $G = g \land \bigwedge_{i \in I} g_{C_i} \land
-    \bigwedge_{j \in J} g_{B_j}$ and
-    $E = e; e_{C_i}^{i \in I}, e_{B_j}^{j \in J}$.
-  \end{enumerate}
-  %
+  \item\label{ab:start} for $i \in I$,\\
+    $a \cap P_{C_i} \neq \emptyset$ and
+    $q_i \goesto{a \cap P_{C_i},\, g_{C_i},\, e_{C_i}} q_i'$
+    is a transition in $C_i$, or\\
+    $a \cap P_{C_i} = \emptyset$ and $q_i = q_i'$
+    (for covenience, we put $g_{C_i} = \true$ and $e_{C_i} = \noop$ in item~\ref{aux1} below);
+  \item for $j \in J$,\\
+    $a \cap P_{B_j} \neq \emptyset$ and
+    $q_j \goesto{a \cap P_{B_j},\, g_{B_j},\, e_{B_j}} q_j'$
+    is a transition in $B_j$, or\\
+    $a \cap P_{B_j} = \emptyset$ and $q_j = q_j'$
+    (for covenience, we put $g_{B_j} = \true$ and $e_{B_j} = \noop$ in item~\ref{aux1} below);
+  \item\label{ab:end}\label{aux1} $g' = g \land \bigwedge_{i \in I} g_{C_i} \land
+    \bigwedge_{j \in J} g_{B_j} \land \varphi_\mu$ and
+    $e' = e; e_{C_i}^{i \in I}, e_{B_j}^{j \in J}$, where    
+%
+    \begin{equation}
+      \label{eq:only1:maxprog:guard}
+      \varphi_\mu = \bigwedge_{
+        \begin{array}{c}
+          q_i^{i \in I} q_j^{j \in J} \goesto{b, h, f} \text{ in }
+          (\IMextend{\Gamma}{P})(\cC \cup \cB)
+          \\
+          a \varsubsetneq b
+        \end{array}
+      } \lnot h
+      \,.
+    \end{equation}
+%
+  \breakenumistart
 
@@
 %
-  \begin{enumerate}
-  \item \label{only1:coord}
-    $(q_i)^{i \in I}
-    \goesto{a \cap P_{C'}, g_{C'}, e_{C'}}
-    (q_i')^{i \in I}$ is a transition in $C'$,
-    or $a \cap P_{C'} = \emptyset$ and $q_i = q_i'$,
-    for all $i \in [1,m]$,
-    $g_{C'} = \true$ and $e_{C'} = \noop$\,;
-  \item for $j \in J$,
+  \breakenumiend
+% 
+  \item \label{a1b:start} \label{only1:coord}
+    $a \cap P_{C'} \neq \emptyset$ and 
+    $(q_i)^{i \in I} \goesto{a \cap P_{C'}, g_{C'}, e_{C'}} (q_i')^{i \in I}$
+    is a transition in $C'$, or\\
+    $a \cap P_{C'} = \emptyset$ and $q_i = q_i'$,
+    for all $i \in [1,m]$
+    (for covenience, we put $g_{C'} = \true$ and $e_{C'} = \noop$ in
+    item~\ref{aux2} below);
+  \item for $j \in J$,\\
+    $a \cap P_{B_j} \neq \emptyset$ and
     $q_j \goesto{a \cap P_{B_j}, g_{B_j}, e_{B_j}} q_j'$
-    is a transition in $B_j$, or
-    $a \cap P_{B_j} = \emptyset$ and $q_j = q_j'$,
-    $g_{B_j} = \true$, and $e_{B_j} = \noop$;
-  \item $G = g \land g_{C'} \land
-    \bigwedge_{j \in J} g_{B_j}$ and
-    $E = e; e_{C'}, e_{B_j}^{j \in J}$.
+    is a transition in $B_j$, or\\
+    $a \cap P_{B_j} = \emptyset$ and $q_j = q_j'$
+    (for covenience, we put $g_{B_j} = \true$ and $e_{B_j} = \noop$ in
+    item~\ref{aux2} below);
+  \item\label{aux2} $g' = g \land g_{C'} \land
+    \bigwedge_{j \in J} g_{B_j} \land \varphi_\mu'$ and
+    $e' = e; e_{C'}, e_{B_j}^{j \in J}$ (with $\varphi_\mu'$ defined as
+    in \eq{only1:maxprog:guard}, but substituting $\{C'\}$ instead of $\cC$).
 %
@@
 % 
-  \item for $i \in I$,
+  \item for $i \in I$,\\
+    $a \cap P_{C_i} \neq \emptyset$ and
     $q_i \goesto{a \cap P_{C_i}, g_{C_i}, e_{C_i}} q_i'$
-    is a transition in $C_i$, or $a \cap P_{C_i} = \emptyset$
-    and $q_i = q_i'$,
-    $g_{C_i} = \true$ and $e_{C_i} = \noop$,
-  \item $g_{C'} = \bigwedge_{i \in I} g_{C_i}$ and
+    is a transition in $C_i$, or\\
+    $a \cap P_{C_i} = \emptyset$ and $q_i = q_i'$,
+    (for covenience, we put $g_{C_i} = \true$ and $e_{C_i} = \noop$ in
+    item~\ref{aux3} below);
+  \item \label{a1b:end} \label{aux3} $g_{C'} = \bigwedge_{i \in I} g_{C_i}$ and
     $e_{C'} = e_{C_i}^{i \in I}$.
@@
   $a \cap P_{C'} = a \cap P_\cC = (a \cap P_A) \cap P_\cC$.
-  Hence, this is also equivalent to
-  $(a \cap P_{C'}, \true, \noop) \in \Gamma_\cC$,
-  which concludes the proof.
+  Hence, by the definition of $\Gamma_\cC$ in the lemma statement,
+  this is also equivalent to
+  $(a \cap P_{C'}, \true, \noop) \in \Gamma_\cC$.
+
+  Thus, conditions \ref{ab:start}\ndash\ref{ab:end} are satisfied iff
+  so are conditions \ref{a1b:start}\ndash\ref{a1b:end} (to see that
+  $\varphi_\mu$ is satisfied iff so is $\varphi_\mu'$, one has to
+  consider the same two sets of conditions, but this time without the
+  additional conjuncts $\varphi_\mu$ and $\varphi_\mu'$ in
+  items~\ref{aux1} and \ref{aux2}, since no priority model is applied
+  to obtain $C'$).  This proves that the transition relations of
+  $\semopen{A(\cB)}$ and $\semopen{A'(\cB)}$ coincide and, therefore,
+  $\semopen{A(\cB)} = \semopen{A'(\cB)}$.
 \end{proof}
+
+\begin{note}
+  \label{rem:upwards:compat}
+  Notice that, since, in the statement of \lem{onlyone}, 
+  %
+  \begin{enumerate}
+  \item the interaction models are the same for both $A$ and $A'$, and
+  \item $P_{C'} = P_\cC$,
+  \end{enumerate}
+  %
+  substituting $A'$ for $A$ preserves upwards compatibility, \ie for any
+  architecture $A''$, holds the following statement: $A$ and $A''$ are
+  upwards compatible if and only if so are $A'$ and $A''$.
+\end{note}
 
@@
   Let $\cB$ be a set of components; let $A_i = (\{C_i\}, V_{A_i},
-  P_{A_i}, \Gamma_i)$, for $i = 1,2$, be two architectures
-  applicable to $\cB$, with one coordinator each, and denote
+  P_{A_i}, \export[A_i], \Gamma_i)$, for $i = 1,2$, be two upwards compatible architectures
+  with one coordinator each, applicable to $\cB$.  Denote
   $P_i = P_{C_i} \cup \bigcup_{B \in \cB} P_B$.
@@
   $\val[\tilde]{}{}$ to
-  $V_1 = V_{C_1} \cup \bigcup_{B \in \cB} V_B$ and
+  $V_i = V_{C_i} \cup \bigcup_{B \in \cB} V_B$ and
   $s' \order s''$.
@@
   component state and a valuation of component variables.  Thus,
-  we have
+  we can expand $s_1 s_2 s \goesto{a, \tilde{\val{}{}}} s_1' s_2' s'$
+  as
 %
@@
 %
-  By \eq{comp:semantics} and \eq{im:int}, this implies
-  $(q_1, q_2, q) \goesto {a, G, E} (q_1', q_2', q')$, with
-%
-  $G = g \land g_1 \land g_2 \land g_b$
+  By \eq{im:sem} and \eq{priority:sem}, this implies
+  that
+  $(q_1, q_2, q) \goesto {a, g', e'} (q_1', q_2', q')$
+  is a transition in $(A_1 \arcomp A_2)(\cB)$, with
+%
+  $g' = g \land g_1 \land g_2 \land g_\cB \land \varphi_\mu$
   and
-  $E = e; (e_1, e_2, e_b)$,
-  where
+  $e' = e; (e_1, e_2, e_\cB)$,
+  where $(a, g, e) \in \Gamma$ (see \eq{arch:composition} for the
+  definition of $\Gamma$);
+%  
+  $g_1$, $g_2$ and $e_1$, $e_2$ are, respectively, the guards and
+  update expressions of the underlying transitions in the coordinating
+  components $C_1$ and $C_2$;
 %    
   \begin{mathpar}
-    g_b = \bigwedge_{B \in \supp{a} \cap \cB} g_B
+    g_\cB = \bigwedge_{B \in \supp{a} \cap \cB} g_B
     \,,
     \and
-    e_b = e_B^{B \in \supp{a} \cap \cB}
+    e_\cB = e_B^{B \in \supp{a} \cap \cB}
+    \,,
   \end{mathpar}
 %
-  and such that $(a, g, e) \in \Gamma$ (see
-  \eq{arch:composition}) and
+  are the compositions of, respectively, the guards and update
+  expressions of the operand components;
+%    
+  \begin{equation}
+    \label{eq:onestep:maxprog:guard}
+    \varphi_\mu = \bigwedge_{
+      \begin{array}{c}
+        (q_1, q_2, q) \goesto{b, h', f'} \text{ in }
+        \bigl(\IMextend{\Gamma}{(P_1 \cup P_2)}\bigr)
+        \bigl(\{C_1, C_2\} \cup \cB\bigr)
+        \\
+        a \varsubsetneq b
+      \end{array}
+    } \lnot h'
+  \end{equation}
+%
+  is the conjunct encoding the maximal progress priority
+  \eq{priority:sem}.  As above for $g'$, for each $(b, h', f')$ in
+  \eq{onestep:maxprog:guard}, $h'$ can be decomposed as $h' = h \land
+  h_1 \land h_2 \land h_\cB$ (without the maximal progress conjunct,
+  since no priority is applied in $\bigl(\IMextend{\Gamma}{(P_1 \cup
+    P_2)}\bigr)\bigl(\{C_1, C_2\} \cup \cB\bigr)$).
+
+  By \eq{comp:semantics}, we also have
 %
@@
     \label{eq:guard}
-    (\val{}{1}, \val{}{2}, \val{}{}) &\models G
+    (\val{}{1}, \val{}{2}, \val{}{}) &\models g'
     \,,
@@
     (\val[\primeit]{}{1}, \val[\primeit]{}{2}, \val[\primeit]{}{})
-    &= \val[\tilde]{}{}[E]
+    &= \val[\tilde]{}{}[e']
     \,,
@@
   If $a \cap P_1 = \emptyset$, then $\supp{a} = \{C_2\}$ and, by
-  \eq{transient} and \defn{im}, $s_1 = s_1'$ and $s = s'$
+  \eq{transient} and \defn{im:sem}, $s_1 = s_1'$ and $s = s'$
   (recall, \defn{im}, that, for $(a,g,e) \in \Gamma$, we have $e
@@
 
-  Denoting $P_b = \bigcup_{B \in \supp{a} \cap \cB} P_B$, we
-  have, by \eq{im:int},
+  By \eq{arch:composition}, for $i=1,2$, there exist $(a \cap P_{A_i},
+  g^i, e^i) \in \Gamma_i$, such that $g = g^1 \land g^2$ and $e = e^1
+  \land e^2$.
+  %% Similarly, for each $(b, h', f')$ in \eq{onestep:maxprog:guard},
+  %% there exist $(b \cap P_{A_i}, h^i, f^i) \in \Gamma_i$, such that
+  %% $h = h^1 \land h^2$ and $f = f^1 \land f^2$.
+%
+  We want to show that the interaction $(a \cap P_1, g^1, e^1)$ is
+  enabled in the state $(q_1, \val{}{1}, q, \val{}{})$ of
+  $\semopen{A_1(\cB)}$.  To this end, we proceed in two steps:
+%
+  \begin{enumerate}
+  \item \label{onestep:proof:im} We show that $(a \cap P_1, g^1,
+    e^1)$ is enabled in the state $(q_1, \val{}{i}, q, \val{}{})$ of
+    $\semopen{(\IMextend{\Gamma_1}{P_1})(\cB)}$.
+  \item \label{onestep:proof:maxp} We show that $(a \cap P_1, g^1,
+    e^1)$ is not inhibited in $\semopen{A_1(\cB)} =
+    \semopen{\mu\bigl((\IMextend{\Gamma_1}{P_1})(\cB)\bigr)}$ by the
+    maximal progress priority.
+  \end{enumerate}
+
+  \paragraph*{Step \ref{onestep:proof:im}}
+  %% Denoting $P_\cB = \bigcup_{B \in \supp{a} \cap \cB} P_B$, 
+  By \eq{im:sem}, we have
 %
@@
     \and
-    q \goesto{a \cap P_b, g_b, e_b} q'
+    q_B \goesto{a \cap P_B, g_B, e_B} q_B',
+    \text{ for each }
+    B \in \cB
     \,.
@@
 
-  By \eq{arch:composition}, for $i=1,2$, there exist
-  $(a \cap P_{A_i}, g^i, e^i) \in \Gamma_i$,
-  such that $g = g^1 \land g^2$ and $e = e^1 \land e^2$.
   By \eq{guard}, we have
-  $(\val{}{1}, \val{}{}) \models g^1 \land g_1 \land g_b$.
-
-  Denoting $\val[\doubletilde]{}{}$ the restriction of
+  $(\val{}{1}, \val{}{}) \models g^1 \land g_1 \land g_\cB$.
+
+  Denoting \todoSB{One tilde is enough}$\val[\doubletilde]{}{1}$ the restriction of
 %
@@
   $(\val[\primeit]{}{1}, \val[\primeit]{}{}) \order
-  \val[\doubletilde]{}{}[e^1; (e_1, e_b)]$.  Notice that all
+  \val[\doubletilde]{}{1}[e^1; (e_1, e_b)]$.  \todoSB{Remove this}\hl{Notice that all
   variables affected by both $e^1$ and $e^2$ must necessarily
-  belong to $\bigcup_{B \in \cB} V_B$.  Hence,
-%
-  $\val[\doubletilde]{}{}[e^1; (e_1, e_b)] =
+  belong to $\bigcup_{B \in \cB} V_B$.}  Hence,
+%
+  $\val[\doubletilde]{}{1}[e^1; (e_1, e_b)] =
   (\val[\primeit]{}{1}, \val[\doubleprimeit]{}{})$ with 
@@
 
-  By \eq{comp:semantics} and \eq{im:int}, we have
-  \[
+  By \eq{comp:semantics} and \eq{im:sem}, we have
+  $
   (q_1, \val{}{1}, q, \val{}{})
-  \goesto{a \cap P_1, \val[\doubletilde]{}{}}
+  \goesto{a \cap P_1, \val[\doubletilde]{}{1}}
   (q_1', \val[\primeit]{}{1}, q, \val[\doubleprimeit]{}{})
-  \,.
-  \]
+  $ in $\semopen{(\IMextend{\Gamma_1}{P_1})(\cB)}$.
+
+  Symmetrically, we have 
+  $
+  (q_2, \val{}{2}, q, \val{}{})
+  \goesto{a \cap P_2, \val[\doubletilde]{}{2}}
+  (q_2', \val[\primeit]{}{2}, q, \val[\doubleprimeit]{}{})
+  $ in $\semopen{(\IMextend{\Gamma_2}{P_2})(\cB)}$.
+
+  \paragraph*{Step \ref{onestep:proof:maxp}}
+  Suppose that $a \cap P_1 \varsubsetneq b_1$, for some interaction
+  $(b_1, h^1, f^1) \in \IMextend{\Gamma_1}{P_1}$ enabled in $(q_1,
+  \val{}{1}, q, \val{}{})$.  Then, by upwards compatibility of $A_1$
+  and $A_2$, there exists $(b_2, h^2, f^2) \in
+  \IMextend{\Gamma_2}{P_2}$, enabled in $(q_2, \val{}{2}, q,
+  \val{}{})$, such that $a \cap P_2 \subseteq b_2$ and $b_2 \cap P_1 =
+  b_1 \cap P_2$.  By \eq{im:extension}, we have $(b_1 \cap P_{A_1},
+  h^1, e^1) \in \Gamma^1$.  Furthermore,
+%
+  \begin{multline*}
+    ((b_1 \cap P_{A_1}) \cup (b_2 \cap P_{A_2}))  \cap P_{A_1} =
+    (b_1 \cap P_{A_1}) \cup (b_2 \cap P_{A_1} \cap P_{A_2}) =\\
+    (b_1 \cap P_{A_1}) \cup ((b_2 \cap P_1) \cap P_{A_1} \cap P_{A_2}) =  
+    (b_1 \cap P_{A_1}) \cup ((b_1 \cap P_2) \cap P_{A_1} \cap P_{A_2}) =\\
+    (b_1 \cup (b_1 \cap P_2 \cap P_{A_2})) \cap P_{A_1} =
+    b_1 \cap P_{A_1} 
+  \end{multline*}
+%
+  Symmetrically, $(b_2 \cap P_{A_2}, h^2, e^2) \in \Gamma^2$ and
+  $((b_1 \cap P_{A_1}) \cup (b_2 \cap P_{A_2})) \cap P_{A_2} = b_2
+  \cap P_{A_2}$.  By \eq{arch:composition}, we then have $((b_1 \cap
+  P_{A_1}) \cup (b_2 \cap P_{A_2}), h^1 \land h^2, f^1 \expmix f^2)
+  \in \Gamma$ and, by \eq{im:extension}, $(b_1 \cup b_2, h^1 \land
+  h^2, f^1 \expmix f^2) \in \IMextend{\Gamma}{(P_1 \cup P_2)}$.
+%
+  Since both $(b_i, h^i, f^i) \in \IMextend{\Gamma_i}{P_i}$ are
+  enabled in the respective states $(q_i, \val{}{i}, q, \val{}{})$, we
+  conclude that $(b_1 \cup b_2, h^1 \land h^2, f^1 \expmix f^2)$ is
+  enabled in $(q_1, \val{}{1}, q_2, \val{}{2}, q, \val{}{})$.
+
+  Since $a \cap P_1 \varsubsetneq b_1$ and $a \cap P_2 \subseteq b_2$,
+  we have $a \varsubsetneq b_1 \cup b_2$.  Thus, $(b_1 \cup b_2, h^1
+  \land h^2, f^1 \expmix f^2)$ contribute to $\varphi_\mu$ in
+  \eq{onestep:maxprog:guard}.  Since $(b_1 \cup b_2, h^1 \land h^2,
+  f^1 \expmix f^2)$ is enabled in $(q_1, \val{}{1}, q_2, \val{}{2}, q,
+  \val{}{})$, we have $(\val{}{1}, \val{}{2}, \val{}{}) \models h^1
+  \land h^2$ and, therefore $(\val{}{1}, \val{}{2}, \val{}{})
+  \not\models \varphi_\mu$, which contradicts \eq{guard}, thereby
+  proving that $(a \cap P_1, g^1, e^1)$ is not inhibited in
+  $\semopen{A_1(\cB)} =
+  \semopen{\mu\bigl((\IMextend{\Gamma_1}{P_1})(\cB)\bigr)}$ by the
+  maximal progress priority.
+
+  The corresponding statement for $(a \cap P_2, g^2, e^2)$ is obtained
+  symmetrically.
 \end{proof}
@@
   $\val[\primeit]{}{1} \models g$.
-  For any $v \in \export(a)$,
+  For any $v \not\in \export(a)$,
   $\val[\primeit]{}{1}(v) = \val{}{1}(v) = \val[\tilde]{}{}(v)$.
@@
 \begin{proof}[Proof of \thm{combining}]
-  By \lem{onlyone}, we can assume that each of the two
+  By \lem{onlyone}, we can assume without loss of generality that each of the two
   architectures has only one coordinating component.  For $i =
@@
   \cup\ \bigcup_{B \in \cB} V_B$.
+%
+  By \rem{upwards:compat}, this does not affect their upwards
+  compatibility, hence neither does this affect the applicability of
+  \lem{onestep} below.
 

### 2018-04-09 2016-Weak-FH-Bisim/WeakBisim.tex
generic pLTS, and corrections ti Figs 1-2-3

--- 2018-03-28 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 To illustrate this work, we use the well-known Alternate bit protocol
-(ABP), that provides safe transport of data between two processes,
+(ABP) \TODO{Ref ?}, that provides safe transport of data between two processes,
 over unsafe media. This protocol has been described and studied using
@@
 way. One can imagine that this could easily be extended using bounded
-integers, as in the Sliding window protocol, or with more complex data
+integers, as in the sliding window protocol, or with more complex data
 structures, in order to verify realistic protocols.
@@
 carrying the message together with a control bit on one way, and an
-acknowledge back form $Q$ to $P$. The media can be perfect (safe), or
+acknowledge back from $receiver$ to $sender$. The media can be perfect (safe), or
 faulty (losing or duplicating messages) as shown in
-Fig. \ref{schema:ABP-media}.
+Fig. \ref{schema:ABP-media}. Remark that the pLTSs shown in
+Fig. \ref{schema:ABP-media} are in fact ``generic'' in the sense that
+they will be instanciated in different ways depending on the number
+and types of the message arguments. This is only a graphical syntax,
+with an obvious semantics for building the corresponding pNets.
+
+Fig. \ref{schema:ABP-composed} \TODO{To be commented}
 

### 2018-04-09 2016-Weak-FH-Bisim/WeakBisim.tex

@@
 %\TODO{Add somewhere a subsection ``running example'' ?}
-
-%%\TODO{rewrite example with new OTs}
-\begin{example}\emph{An open-transition.}
-  \label{OT:ABP}
-  The \texttt{Protocol} pNet of Fig. \ref{schema:ABP-composed} has 4 controllers and no holes. One of its possible open-transition (the sender sending $(m,b)$ to the medium) is:
-
- \smallskip
- $  OT_2  = \openrule{
-%                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
-   %                           \xrightarrow{in(?m,?b)}_{M1}
-      \emptyset; Pred=[m=s_1\_m, b=s_1\_sb];  Post=\{m_1\_m:=m, m_1\_b:=b\}
-                      }
-  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
-    {Prot_1 \OTarrow{\tau} Prot_2}
-    $
-
-    \smallskip
-    Here the global states $Prot_1$ and $Prot_2$ encode the states of
-    the 4 pLTS composing the system, namely
-    $Prot_1=\ostate{s_1,m_0,m_0,r_0}$ and
-    $Prot_2=\ostate{s_2,m_1,m_0,r_0}$, showing that the sender and the
-    first medium have evolved during this transition.
-    The predicate $Pred$ involves the state variables $s_1\_m$ and
-    $s_1\_sb$ of the sender, while the assignment $Post$ sets the
-    state variables of the medium.
-
-    \smallskip
-At the upper level, the $ABP$ pNet has 2 holes and and $Protocol$ has
-a subnet. One of its possible transition (synchronizing the hole $P$
-with the $Protocol$) is:
-
- \smallskip
- $  OT_1  = \openrule{
-%                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
-%                            \xrightarrow{in(?m,?b)}_{M1}
-      \{\xrightarrow{send(m)}_P\}; Pred=True; Post=\{s1\_m:=m\}
-                      }
-  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
-    {ABP_1 \OTarrow{\underline{send(m)}} ABP_2}
-    $
-
-    \smallskip
-    The global states $ABP_1$ and $ABP_2$ have the same structure than
-    $Prot_1$ and $Prot_2$, as the holes have no states. The assignment
-    $Post$ uses a variable from the action of hole $P$ to set the
-    value of the sender state variable $s1\_m$.
-\end{example}
 
@@
 step.
+
+%%\TODO{rewrite example with new OTs}
+\begin{example}\emph{An open-transition.}
+  \label{OT:ABP}
+  The \texttt{Protocol} pNet of Fig. \ref{schema:ABP-composed} has 4 controllers and no holes. One of its possible open-transition (the sender sending $(m,b)$ to the medium) is:
+
+ \smallskip\noindent
+ $  OT_2  = \openrule{
+%                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
+   %                           \xrightarrow{in(?m,?b)}_{M1}
+      \emptyset; Pred=[m=s_1\_m, b=s_1\_sb, v=\tau];  Post=\{m_1\_m:=m, m_1\_b:=b\}
+                      }
+  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
+    {\ostate{s_1,m_0,m_0,r_0} \OTarrow{v} \ostate{s_2,m_1,m_0,r_0}}
+    $
+
+    \smallskip
+    Note that the global states shows how the sender and the
+    first medium have evolved during this transition, the sender
+    moving from $s_1$ to $s_2$, and the first (forward) medium from
+    $m_0$ to $m_1$.
+    The predicate $Pred$ involves the state variables $s_1\_m$ and
+    $s_1\_sb$ of the sender, while the assignment $Post$ sets the
+    state variables of the medium.
+
+    \smallskip
+At the upper level, the $ABP$ pNet has 2 holes and and $Protocol$ has
+a subnet. One of its possible transition (synchronizing the hole $P$
+with the $Protocol$) is:
+
+ \smallskip\noindent
+ $  OT_1  = \openrule{
+%                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
+%                            \xrightarrow{in(?m,?b)}_{M1}
+      \{\xrightarrow{b_P}_P\}; Pred=[b_P=send(m)\land v=\underline{send(m)}]; Post=\{s1\_m:=m\}
+                      }
+  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
+    {\ostate{s_0,m_0,m_0,r_0} \OTarrow{v} \ostate{s_1,m_0,m_0,r_0}}
+    $
+
+    \smallskip
+    The global states here have the same structure than
+    in $OT\_2$, as the holes have no states. The assignment
+    $Post$ uses a variable from the action of hole $P$ to set the
+    value of the sender state variable $s1\_m$.
+\end{example}
 

### 2018-04-10 2016-Weak-FH-Bisim/WeakBisim.tex

--- 2018-04-09 2016-Weak-FH-Bisim/WeakBisim.tex
@@
   between INRIA and ECNU, Shanghai}}
-\author{ Ludovic Henrio\inst{1}  \ \ \  Eric Madelaine\inst{1,2} \ \ \ Min Zhang\inst{3}}
+\author{ Ludovic Henrio\inst{1}  \ \ \  Eric Madelaine\inst{1,2} \ \ \ Rabéa}
 \institute{Univ. of Nice Sophia Antipolis, CNRS, UMR 7271, 06900 Sophia Antipolis, France
 	\and INRIA Sophia Antipolis M\'edit\'erann\'ee, BP 93, 06902 Sophia Antipolis, France
-\and Shanghai Key Laboratory of Trustworthy Computing, ECNU, China}
+}
 \date{}                                           % Activate to display a given date or no date
@@
 \section{Status and TODO list}
-Improve and simplify Tr2
-
-X notation guards in  SV
+TODOS et deadline
+
+Ludo
+\begin{itemize}
+\item rewrite Tr2 and open transition with actions
+\item $v'\to \alpha'$ dans pred sv et enlever l exists
+\item $\beta$ ou $b$
+\item propager Tr2 dans l annexe
+\item add simple equivalence on OT
+\end{itemize}
+=== 18 Avril
+\medskip
+
+Eric
+\begin{itemize}
+\item re-ecrire transitions page 14 comment les presenter?
+\item arbre de deduction
+\item exemple avec actions
+\end{itemize}
+=== 20 Avril?
+\medskip
+
+Rabea
+\begin{itemize}
+\item uniformiser p et P pour les pnets
+\item relectures
+\end{itemize}
+=== en parallele
 
@@
 	\begin{mathpar}
-	\inferrule*[myfraction=\reddottedrule]
+	\openrule
 	{	\{\beta_j\}^{j\in J}, \Pred, \Post}
@@
 			\models
-			\mprset{myfraction=\reddottedrule}\inferrule
+			\openrule
 			{\emptyset ,
@@
 	\forall m\!\!\in\!\! I_1. {\pNet_m 
-	\models\mprset{myfraction=\reddottedrule}\inferrule
+	\models\openrule
     	{
@@
     	 \models
-    	\mprset{myfraction=\reddottedrule}\inferrule
+    	\openrule
     	{\emptyset, \Pred_m, \Post_m}
@@
     	\models
-    	{\mprset{myfraction=\reddottedrule}\inferrule
+    	{\openrule
     		{
@@
  \begin{mathpar}
-     \inferrule*[myfraction=\reddottedrule]
+     \openrule
          {
@@
 %    \left( fresh \ \overline{\alpha_i}, \overline{b_j}, v_x.\ \
-    \inferrule*[myfraction=\reddottedrule]
+    \openrule
          {
@@
  \begin{mathpar}
- \inferrule*[myfraction=\reddottedrule]
+ \openrule
          {
@@
  \begin{mathpar}
-    \inferrule*[myfraction=\reddottedrule]
+    \openrule
          {
@@
 
-       	\inferrule*[myfraction=\reddottedrule]
+       	\openrule
        	{
@@
        	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
-       	\inferrule*[myfraction=\reddottedrule]
+       	\openrule
        	{
@@
 		\models
-		{\mprset{myfraction=\reddottedrule}\inferrule
+		{\openrule
 			{
@@
 		\begin{mathpar}
-		P\models{\mprset{myfraction=\reddottedrule}\inferrule
+		P\models{\openrule
 			{
@@
 		%\[
-		Q\models{\mprset{myfraction=\reddottedrule}\inferrule
+		Q\models{\openrule
 			{
@@
 \[
-\pNet_m \models\mprset{myfraction=\reddottedrule}\inferrule
+\pNet_m \models\openrule
     	{
@@
 $L_{j_0}=L_Q$, and $J_{j_0}=	J\cap\Holes(Q)$):\\[-2ex]
-	\[Q\models{\mprset{myfraction=\reddottedrule}\inferrule
+	\[Q\models{\openrule
 		{
@@
 %\[
-P\models{\mprset{myfraction=\reddottedrule}\inferrule
+P\models{\openrule
 	{
@@
 %\[
-Q\models{\mprset{myfraction=\reddottedrule}\inferrule
+Q\models{\openrule
 	{
@@
 	\models
-	{\mprset{myfraction=\reddottedrule}\inferrule
+	{\openrule
 		{
@@
     	\forall m\!\!\in\!\! I_1\uplus\{j_0\}. {\pNet_m 
-    	\models\mprset{myfraction=\reddottedrule}\inferrule
+    	\models\openrule
     	{
@@
  \\[-2ex]     
- \[P[Q]_{j_0}\models\mprset{myfraction=\reddottedrule}\inferrule
+ \[P[Q]_{j_0}\models\openrule
  {
@@
  	\begin{mathpar}
- P\models{\mprset{myfraction=\reddottedrule}\inferrule
+ P\models{\openrule
  	{
@@
  }\\
- Q\models{\mprset{myfraction=\reddottedrule}\inferrule
+ Q\models{\openrule
  	{
@@
  \begin{mathpar}
- Q'\models\mprset{myfraction=\reddottedrule}\inferrule
+ Q'\models\openrule
  {
@@
  \models
- {\mprset{myfraction=\reddottedrule}\inferrule
+ {\openrule
  	{
@@
 \\[-2ex]     
-	\[P[Q]_{j_0}\models\mprset{myfraction=\reddottedrule}\inferrule
+	\[P[Q]_{j_0}\models\openrule
 	{
@@
 			\begin{mathpar}
-				P\models{\mprset{myfraction=\reddottedrule}\inferrule
+				P\models{\openrule
 				{
@@
 			}\\
-			Q\models{\mprset{myfraction=\reddottedrule}\inferrule
+			Q\models{\openrule
 				{
@@
 			%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
-			P'\models\mprset{myfraction=\reddottedrule}\inferrule
+			P'\models\openrule
 			{
@@
 				\models
-				{\mprset{myfraction=\reddottedrule}\inferrule
+				{\openrule
 					{

### 2018-04-18 2017-Xudong-SMT/AVOCS-2018.tex
Avocs first version

--- 2018-01-23 2017-Xudong-SMT/FM-2018-extended.tex
@@
 \newcommand{\raisem@th}[3]{\raisebox{#1}{$#2#3$}}
+
+%definitions from ``Arch-pNets''
+\newcommand{\cA}{\ensuremath{\mathcal{A}}}
+\newcommand{\fA}{\ensuremath{\mathsf{A}}}
+\newcommand{\sA}{\ensuremath{\mathbb{A}}}
+\newcommand{\cB}{\ensuremath{\mathcal{B}}}
+\newcommand{\fB}{\ensuremath{\mathsf{B}}}
+\newcommand{\sB}{\ensuremath{\mathbb{B}}}
+\newcommand{\cC}{\ensuremath{\mathcal{C}}}
+\newcommand{\sC}{\ensuremath{\mathbb{C}}}
+\newcommand{\cD}{\ensuremath{\mathcal{D}}}
+\newcommand{\fD}{\ensuremath{\mathsf{D}}}
+\newcommand{\sD}{\ensuremath{\mathbb{D}}}
+\newcommand{\cE}{\ensuremath{\mathcal{E}}}
+\newcommand{\sE}{\ensuremath{\mathbb{E}}}
+\newcommand{\cF}{\ensuremath{\mathcal{F}}}
+\newcommand{\cG}{\ensuremath{\mathcal{G}}}
+\newcommand{\cH}{\ensuremath{\mathcal{H}}}
+\newcommand{\cI}{\ensuremath{\mathcal{I}}}
+\newcommand{\sI}{\ensuremath{\mathbb{I}}}
+\newcommand{\cM}{\ensuremath{\mathcal{M}}}
+\newcommand{\cN}{\ensuremath{\mathcal{N}}}
+\newcommand{\sN}{\ensuremath{\mathbb{N}}}
+\newcommand{\cP}{\ensuremath{\mathcal{P}}}
+\newcommand{\sP}{\ensuremath{\mathbb{P}}}
+\newcommand{\cQ}{\ensuremath{\mathcal{Q}}}
+\newcommand{\sQ}{\ensuremath{\mathbb{Q}}}
+\newcommand{\cR}{\ensuremath{\mathcal{R}}}
+\newcommand{\sR}{\ensuremath{\mathbb{R}}}
+\newcommand{\cS}{\ensuremath{\mathcal{S}}}
+\newcommand{\sS}{\ensuremath{\mathfrak{S}}}
+\newcommand{\cT}{\ensuremath{\mathcal{T}}}
+\newcommand{\fT}{\ensuremath{\mathsf{T}}}
+\newcommand{\sT}{\ensuremath{\mathbb{T}}}
+\newcommand{\cV}{\ensuremath{\mathcal{V}}}
+\newcommand{\fV}{\ensuremath{\mathsf{V}}}
+\newcommand{\sV}{\ensuremath{\mathbb{V}}}
+\newcommand{\sZ}{\ensuremath{\mathbb{Z}}}
+
+\newcommand{\ordbool}{\ensuremath{\sB^{<}}}
+\newcommand{\data}{\ensuremath{\sD}}
+\newcommand{\signature}{\ensuremath{\Sigma}}
+\newcommand{\variables}{\ensuremath{\cV}}
+\newcommand{\Talg}{\ensuremath{\cT_{\signature,\variables}}}
+\newcommand{\actions}[1]{\ensuremath{\cA_{#1}}}
+\newcommand{\guards}[1]{\ensuremath{\ordbool_{#1}}}
+\newcommand{\exprs}[1]{\ensuremath{\sE_{#1}}}
+\newcommand{\boolexprs}[1]{\ensuremath{\sB_{#1}}}
+\newcommand{\assigns}[1]{\ensuremath{\sA_{#1}}}
+\newcommand{\valuations}[1]{\ensuremath{\data^{#1}}}
+\newcommand{\val}[3][]{\ensuremath{#1{\sigma}^{#2}_{#3}}}
+
 \makeatother
@@
 
+%% \begin{definition}[pNets]\label{def-pnets}
+%% A pNet is a hierarchical structure, whereof the leaves are pLTSs and holes:
+%% $\pNet::= pLTS~|~\mylangle \pNet_i^{i\in I}, S_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle$,
+%% where
+%% \begin{itemize}
+%% \item[$\bullet$] %\noteEM{Pire que ca, $\I$ n'est pas
+%%                  %defini...}\noteSB{Why is one $\I$ and the other
+%%   %$\I_\P$?}
+%%   $I$ and $J$ are the sets over which are indexed sub-pNets and holes, respectively, such that: $I\cap J=\emptyset$ and  $I\cup J\neq\emptyset$.
+
+%% \item[$\bullet$] $\pNet_i^{i\in I}$ is a family of sub-pNets.
+
+%% \item[$\bullet$] $S_j \subseteq \AlgA$ is a set of action terms,
+%%   denoting the $\Sort$\footnote{The definition of $Sorts$ (the
+%%     set of actions of a Hole  
+%%   or pNet), and also of $Leaves$ and $Holes$ (respectively all pLTSs
+%%   and all holes in a pNet), can be found in \cite{henrio:Forte2016}.}
+%%   of hole $j$.
+
+%% \item[$\bullet$] $\symb{SV}_k^{k\in K}$, with $K\in\I_\P$, is a set of
+%%   synchronization vectors: for each $k\!\in\! K$,
+%%   $\symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k$ where
+%%   $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
+%%   $\forall i\!\in\! I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$
+%% %  \noteSB{What is the sort of a pNet? Should we define $\Sort(\pNet)
+%% %    \triangleq \{\Label(\symb{SV}_k\,|\,k \in K\}$?}
+%%   , 
+%%   $\forall j\!\in\!
+%%   J_k.\,\alpha_{j}\!\in\!S_j$, and $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
+%%   J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
+%%   $\Label(\symb{SV}_k) = \alpha'_k$.
+%% \end{itemize}
+%% \end{definition}
+
   \begin{definition}[pNets]\label{def-pnets}
-A pNet is a hierarchical structure, whereof the leaves are pLTSs and holes:
-$\pNet::= pLTS~|~\mylangle \pNet_i^{i\in I}, S_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle$,
+    A pNet is a hierarchical structure where leaves are pLTSs and holes:
+   %%  \footnote{Typing can 
+%% be added to pNets by defining and checking their interfaces, called 
+%% sort~\cite{HMZ-FORTE2016}}
+$\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, J, \symb{SV}_k^{k\in 
+K}\myrangle$
 where
 \begin{itemize}
-\item[$\bullet$] %\noteEM{Pire que ca, $\I$ n'est pas
-                 %defini...}\noteSB{Why is one $\I$ and the other
-  %$\I_\P$?}
-  $I$ and $J$ are the sets over which are indexed sub-pNets and holes, respectively, such that: $I\cap J=\emptyset$ and  $I\cup J\neq\emptyset$.
-
-\item[$\bullet$] $\pNet_i^{i\in I}$ is a family of sub-pNets.
-
-\item[$\bullet$] $S_j \subseteq \AlgA$ is a set of action terms,
-  denoting the $\Sort$\footnote{The definition of $Sorts$ (the
-    set of actions of a Hole  
-  or pNet), and also of $Leaves$ and $Holes$ (respectively all pLTSs
-  and all holes in a pNet), can be found in \cite{henrio:Forte2016}.}
-  of hole $j$.
-
-\item[$\bullet$] $\symb{SV}_k^{k\in K}$, with $K\in\I_\P$, is a set of
-  synchronization vectors: for each $k\!\in\! K$,
-  $\symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k$ where
-  $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
-  $\forall i\!\in\! I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$
-%  \noteSB{What is the sort of a pNet? Should we define $\Sort(\pNet)
-%    \triangleq \{\Label(\symb{SV}_k\,|\,k \in K\}$?}
-  , 
-  $\forall j\!\in\!
-  J_k.\,\alpha_{j}\!\in\!S_j$, and $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
+\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets;
+%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which 
+%sub-pNets are indexed.
+
+\item[$\bullet$] $J$ is a set of indexes, called \emph{holes}.
+$I$ and $J$ are \emph{disjoint}: $I\!\cap\! J=\emptyset$,  $I\!\cup\! J\neq\emptyset$
+%\item[$\bullet$] $\Sort_j \subseteq \AlgAS$ is a set of action terms, denoting the 
+%\emph{sort} of
+%hole $j$.
+
+\item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
+  synchronisation vectors ($K\in\I_\P$). $\forall k\!\in\! K,
+  \symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k\,|\,g_k$, where
+  $\alpha'_k\in \actions{\variables}$, $I_k\subseteq I$, $J_k\subseteq J$, and 
+  $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
   J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
-$\Label(\symb{SV}_k) = \alpha'_k$.
+$\alpha'_k$. The Boolean expression $g_k $, such that $\vars(g_k)\subseteq \bigcup_{l\in 
+I_k\uplus J_k}{\vars({\alpha_l})}$, is a guard associated to the vector.
 

### 2018-04-18 2017-Xudong-SMT/AVOCS-2018.tex
comments of Rev 2

@@
 open systems encoded as pNets. The equivalence between pNets is
-"FH-bisimulation" taking the 
-predicate of the open transitions into account each time matching such
+"FH-bisimulation" \cite{henrio:Forte2016}, a dedicated version of
+symbolic bisimulation taking the  
+predicate of the open transitions into account when matching such
 open transitions. We foresee that the interplay with the SMT solver
@@
 shows the full result of the semantic computation on the running example.
-Finally we conclude and discuss perspectives.
+Finally we conclude and discuss perspectives in Section
 \ref{section:conclusion}.
@@
 which can only be modified by the assignment in transitions targeting this state. 
-A global state variable of a pLTS is a variable $x$ satisfying
-$\forall s\!\in\! S .\, x\!\in\! \vars(s)$. 
+A global state variable of a pLTS is a state variable defined in all states.
+% $x$ satisfying $\forall s\!\in\! S .\, x\!\in\! \vars(s)$. 
 %
@@
 $\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, J, \symb{SV}_k^{k\in 
-K}\myrangle$
+K}\myrangle$, with $I, J, K$ potentialy infinite,
 where
@@
 	\label{def:OpenTransitions}
-	An \emph{open transition} over a set  $\langle S_i,s_{0 i}, \rightarrow_i\rangle^{i\in
+	An \emph{open transition} $OT$ over a set  $\langle S_i,s_{0 i}, \rightarrow_i\rangle^{i\in
 	I}$ of LTSs, a
-	set $J$ of holes with sorts $Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is a structure of the form:	
+	set $J$ of holes, %with sorts $Sort_j^{j\in J}$
+        and a set of states $\mathcal{S}$ is a structure of the form:	
 	\begin{mathpar}
@@
 	\end{mathpar}
-	where $s, s'\in\mathcal{S}$ and, for all
-        $i\in I$, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the
-	LTS $\langle S_i,s_{0 i}, \rightarrow_i\rangle$, and $\xrightarrow{b_j}_j$
-        is a transition of the hole $j$, for any action $b_j$ in the
-        sort $Sort_j$. \Pred\ is a predicate
+	where $s, s'\in\mathcal{S}$, the $a_i, b_j, \alpha$ are
+        action expressions, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is
+        a transition of the 
+	LTS $\langle S_i,s_{0 i}, \rightarrow_i\rangle$, $b_j$
+        is an action of the hole $j$, and $\alpha$ is the resulting action
+        of $OT$. \Pred\ is a predicate
 	over the variables of the terms, labels, and states $s_i$,
-        $b_j$, $s$, $v$. \Post\ is a set of equations that  
+        $b_j$, $s$, $\alpha$. \Post\ is a set of equations that  
 	hold \emph{after the open transition}, represented as a
@@
 Let
-$\mylangle\overline{\pNet},\overline{S},\symb{SV}_k^{k\in K} \myrangle$
+$\mylangle\overline{\pNet},J,\symb{SV}_k^{k\in K} \myrangle$
 be a pNet. Consider a synchronization vector $SV_k$, for $k\in K$. We build a
@@
 App.~\ref{appendix:semRules}.
+
+In \cite{henrio:Forte2016} we also
+proved that a pNet with finitely many pLTSs, holes, and
+synchronisation vectors, and with finite pLTSs, has a finite
+semantics. But all the elements of such pNets and open automata being
+symbolic, they can represent many classes of unbounded systems.
 
@@
 \While{!$\mathit{isEmpty}(U)$}
-	\State Choose $S$ in $U\setminus E$; add $S$ in $E$;
+	\State Choose $S$ in $U$; remove $S$ from $U$, add $S$ to $E$;
         %\qquad \hl{\textbackslash\textbackslash~SB: was `` Choose $S$ in $U$ ''}
-	\State $\mathit{OT} = \mathit{MakeTransitions}(P, S)$;
-        \State Store $\mathit{OT}$ in $L$; 
-	\For {each $\mathit{OT} \in L$}
-        \State Let $T$ be the target global state of $\mathit{OT}$
-	\IfThen{($T \not\in U$ \&\& $T \not\in E$)}{Add $T$ into $U$;}
+	\State $\mathit{OTs} = \mathit{MakeTransitions}(P, S)$;
+%%        \State Store $\mathit{OT}$ in $L$; 
+	\For {each $\mathit{OT} \in \mathit{OTs}$}
+        Check satisfiability of $\mathit{OT}$ using the SMT solver;
+        \IfThen {$SAT(\mathit{OT})$}
+                {\State \{Add $\mathit{OT}$ to $L$;
+                  \State Let $S'$ be the target global state of $\mathit{OT}$
+	          \IfThen{($S' \not\in U \cup E$)}{Add $S'$ into $U$;}
+                  \}}
 	\EndFor
 \EndWhile
-\State Prune the unsatisfiable open transitions in $L$ using the SMT solver;
-\State \Return $\mathit{OA}=\mathit{Reachable}(\mathit{InitState}(P),L)$;
+%%\State Prune the unsatisfiable open transitions in $L$ using the SMT solver;
+\State \Return $\mathit{OA}=(\mathit{InitState}(P),L)$;
 
@@
 %
-The final open automaton is computed as the set of global states,
-reachable after pruning the unsatisfiable OTs.
+The final open automaton includes all satisfiable OTs, and the set of
+reachable global states.
+
 %

### 2018-04-18 2016-Weak-FH-Bisim/WeakBisim.tex
2 level logic, sv, actions in OT def

@@
 \item add simple equivalence on OT
+\item[x] explain the 2 level logic
 \end{itemize}
@@
 	{	\{\beta_j\}^{j\in J}, \Pred, \Post}
-	{s \OTarrow {v}s'}
+	{s \OTarrow {\alpha}s'}
 	\end{mathpar}
-	Where $s, s'\in\mathcal{S}$ and $b_j$
-        is a transition of the hole $j$, for any action $b_j$ in the
-        sort $\Sort_j$. $v$ is a variable denoting the resulting action
+	Where $s, s'\in\mathcal{S}$ and $\beta_j$
+        is a transition of the hole $j$, with $\beta_j\in\Sort_j$. $\alpha$ is an action 
+        label denoting the resulting action
         of this open transition. \Pred\ is a predicate 
 	over the different variables of the
-	terms, labels, and states $s_i$, $\beta_j$, $s$, $v$. \Post\ is a set of equations 
+	terms, labels, and states $s_i$, $\beta_j$, $s$, $\alpha$. \Post\ is a set of 
+	equations 
 	that 
@@
 %\TODO{Add somewhere a subsection ``running example'' ?}
+
+It is important to understand the difference between the red dotted rule and a normal 
+inference rule. They correspond to two different logical levels.
+ The open transition is itself a logical implication, but using a simple logic (with the 
+ expressive power that is given to the predicate and necessary include logical 
+ propositions and equality). We differentiate classical (black) inference rules that use 
+ an expressive logic and are paper rules from open transition rules that use a simpler 
+ logic, 
+ will be embedded into automata transitions, and could typically be handled in a 
+ mechanical way.
 
@@
 the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
-\[\Pred_{\symb{sv}}(SV, \alpha_i^{i\in I}, \beta_j^{j\in J}, v)\Leftrightarrow \bigg(
-\begin{array}{l}
-\exists {(\alpha'_i)}^{i\in I},
-{(\beta'_j)}^{j\in J},v'.\, SV=\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} {v'} 
-{e_b}
-\\~~\land
-\forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, \beta_j=\beta'_j \land v=v' 
+\[\begin{array}{l}\Pred_{\symb{sv}}(\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
+{\alpha'} 
+{e_b}, \alpha_i^{i\in I}, \beta_j^{j\in J}, \alpha)\Leftrightarrow \\~\qquad\qquad%\bigg(
+%
+%\exists {(\alpha'_i)}^{i\in I},
+%{(\beta'_j)}^{j\in J},v'.\, SV=
+%\\~~\land
+\forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, \beta_j=\beta'_j \land 
+\alpha=\alpha' 
 \land e_b
-\end{array} \bigg)\]
+\end{array} 
+%\bigg)
+\]
 

### 2018-04-19 2016-Weak-FH-Bisim/WeakBisim.tex
rewrite Tr2 and open transition with actions; $v'\to \alpha'$ dans pred sv et enlever l exists; $\beta$ a la place de b et v; propager Tr2 dans l annexe; preuves de l annexe avec nouvelles notations

@@
 
+\TODO{should we use iff/implies or LeftRightArrow/Rightarrow}
+
 Ludo
 \begin{itemize}
-\item rewrite Tr2 and open transition with actions
-\item $v'\to \alpha'$ dans pred sv et enlever l exists
-\item $\beta$ ou $b$
-\item propager Tr2 dans l annexe
+\item[x] rewrite Tr2 and open transition with actions
+\item[x] $v'\to \alpha'$ dans pred sv et enlever l exists
+\item[x] $\beta$ ou $b$
+\item[x] propager Tr2 dans l annexe
 \item add simple equivalence on OT
@@
 
+Synchronisation vectors are identified modulo renaming of variables that appear in their 
+action terms.
+
 A pNet $Q$ is \emph{closed} if it has no hole: $\Holes(Q)=\emptyset$; else it
@@
 	\openrule
-	{	\{\beta_j\}^{j\in J}, \Pred, \Post}
+	{	\beta_j^{j\in J}, \Pred, \Post}
 	{s \OTarrow {\alpha}s'}
@@
    %                           \xrightarrow{in(?m,?b)}_{M1}
-      \emptyset; Pred=[m=s_1\_m, b=s_1\_sb, v=\tau];  Post=\{m_1\_m:=m, m_1\_b:=b\}
+      \emptyset; Pred=[m=s_1\_m, b=s_1\_sb];  Post=\{m_1\_m:=m, m_1\_b:=b\}
                       }
   %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
-    {\ostate{s_1,m_0,m_0,r_0} \OTarrow{v} \ostate{s_2,m_1,m_0,r_0}}
+    {\ostate{s_1,m_0,m_0,r_0} \OTarrow{\tau} \ostate{s_2,m_1,m_0,r_0}}
     $
@@
 %                            \xrightarrow{in(?m,?b)}_{M1}
-      \{\xrightarrow{b_P}_P\}; Pred=[b_P=send(m)\land v=\underline{send(m)}]; Post=\{s1\_m:=m\}
+      (P\mapsto send(m)); Pred=[m=m']; Post=\{s1\_m:=m\}
                       }
   %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
-    {\ostate{s_0,m_0,m_0,r_0} \OTarrow{v} \ostate{s_1,m_0,m_0,r_0}}
+    {\ostate{s_0,m_0,m_0,r_0} \OTarrow{\underline{send(m')}} \ostate{s_1,m_0,m_0,r_0}}
     $
@@
 %set of Holes and the set of Leaves.
-The semantics   regularly instantiates \emph{fresh} variables, and uses a
-\emph{clone} operator that clones a term replacing each variable with a
-fresh one.
+The semantics    instantiates \emph{fresh} variables, additionally, for an action 
+$\alpha$, $\fresh(\alpha)$ means all variables in $\alpha$ are fresh.
 
@@
     	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
-k\!\in\! K \qquad SV_k \!=\! \SV{\alpha_m^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} \\
+k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
+\\
 \\     	
@@
     	{
-    	\{{\beta_{j}}\}^{j\in J_m}, \Pred_m, \Post_m}
-    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
+    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
+    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
     		\ostate{(s_i^\prime)^{i\in L_m}}} }	
@@
     	{\emptyset, \Pred_m, \Post_m}
-    	{\ostate{s_m} \OTarrow {v_m}
+    	{\ostate{s_m} \OTarrow {\alpha_m}
     		\ostate{s_m'}} }\\\\
@@
     	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
-    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in (I_1\uplus I_2)},\beta_j^{j\in J},v)\\ 
+    	\Pred_{\symb{sv}}(SV_k,\alpha_m^{m\in (I_1\uplus I_2)},\beta_j^{j\in J},\alpha)\\ 
     		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
     	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
-    {\tt fresh}(\alpha_m,\alpha',\beta_j,v) 
+    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
     }
@@
     		{
-    		\{{\beta_j}\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_1\uplus I_2} 
+    		{\beta_j}^{j\in J^\prime}, \Pred, \uplus_{m\in I_1\uplus I_2} 
     		\Post_m}
-    		{\ostate{s_i^{i\in L}} \OTarrow {v}
+    		{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
     			\ostate{(s_i^\prime)^{i\in L}}}
@@
          {
-           \{{\beta_j}\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
-         {s \OTarrow {v} s'}
+           \beta_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
+         {s \OTarrow {\alpha} s'}
 
@@
          {
-           \{{\beta_{j x}}\}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {t \OTarrow {v_x} t_x}
+           \beta_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {t \OTarrow {\alpha_x} t_x}
 %         \right)
@@
    \left( \forall j. \beta_j=\beta_{jx}  \Rightarrow \Pred_{OT_x}
-     \land v\!=\!v_x \land  
+     \land \alpha\!=\!\alpha_x \land  
      \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
@@
          {
-           \{{\beta_j}\}^{j\in J_1},\Pred,\Post}
-         {s \OTWeakarrow {v} s'}
+           \beta_j^{j\in J_1},\Pred,\Post}
+         {s \OTWeakarrow {\alpha} s'}
          \in \mathcal{T}^*
@@
          {
-           \{{\beta_{j x}}\}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {t \OTWeakarrow {v_x} t_x}
+           \beta_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {t \OTWeakarrow {\alpha_x} t_x}
 \end{mathpar}
@@
        	{
-       		\{{\beta_j}\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
-       	{s \OTarrow {v} {s}'}
+       		\beta_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
+       	{s \OTarrow {\alpha} {s}'}
 
@@
        	{
-       		\{{\beta_{j p x}}\}^{j\in J_{px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
-       	{t_p \OTarrow {v_{px}} t_{p x}}
+       		\beta_{j p x}^{j\in J_{px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
+       	{t_p \OTarrow {\alpha_{px}} t_{p x}}
        	%         \right)
@@
        	\left( \forall j. \beta_j=\beta_{jpx}  \Rightarrow \Pred_{OT_{px}}
-       	\land v\!=\!v_{px} \land
+       	\land \alpha\!=\!\alpha_{px} \land
        	\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)$\\
@@
        	{
-       		\{{\beta_{j p x y}}\}^{j\in J_{pxy}}, 
+       		\beta_{j p x y}^{j\in J_{pxy}}, 
        		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
-       	{u \OTarrow {v_{pxy}} u_{pxy}}
+       	{u \OTarrow {\alpha_{pxy}} u_{pxy}}
        	%         \right)
@@
        	\left( \forall j. \beta_{jpx}=\beta_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
-       	\land v_{px}\!=\!v_{pxy} \land
+       	\land \alpha_{px}\!=\!\alpha_{pxy} \land
        	\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$\\.
@@
        		\left( \forall j. \beta_j=\beta_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
-       		\land v\!=\!v_{pxy} \land
+       		\land \alpha\!=\!\alpha_{pxy} \land
        		\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
        	\end{small}
-\TODO{From we will add notation (1) and (2)}        	
+\TODO{From we will add notation (1) and (2)}   \LUDO{I do not remember what this TOD 
+means, Rabea?}      	
        	We have, for all $p$
@@
        		\left( \forall j. \beta_j=\beta_{jpx}  \Rightarrow \Pred_{OT_{px}}
-       		\land v\!=\!v_{px} \land
+       		\land \alpha\!=\!\alpha_{px} \land
        		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\land\Pred_{p,u}\\
@@
        		(\Pred_{OT_{px}}\land\Pred_{p,u})
-       		\land v\!=\!v_{px} \land
+       		\land \alpha\!=\!\alpha_{px} \land
        		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\\
@@
        		\big( \forall j'. \beta_{j'px}=\beta_{j'pxy}  \Rightarrow \Pred_{OT_{pxy}}
-       		\land v_{px}\!=\!v_{pxy}\\\hspace{3em}~ \land
+       		\land \alpha_{px}\!=\!\alpha_{pxy}\\\hspace{3em}~ \land
        		\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\big))
-       		\land v\!=\!v_{px} \land
+       		\land \alpha\!=\!\alpha_{px} \land
        		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\\
@@
        		\Pred_{OT_{pxy}}
-       		\land v\!=v_{px}\!=\!v_{pxy}\\\hspace{3em}~ \land
+       		\land \alpha\!=\alpha_{px}\!=\!\alpha_{pxy}\\\hspace{3em}~ \land
        		\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}
@@
 \Pred_{OT_{pxy}}
-\land v\!=v_{px}\!=\!v_{pxy}\\~\hspace{3em}~ \land
+\land \alpha\!=\alpha_{px}\!=\!\alpha_{pxy}\\~\hspace{3em}~ \land
 \Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\big)\big)
@@
 \left( \forall j. \beta_j=\beta_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
-\land v\!=\!v_{pxy} \land
+\land \alpha\!=\!\alpha_{pxy} \land
 \Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
@@
 			{
-				\{{\beta_j}\}^{j\in J}, \Pred,  
+				\beta_j^{j\in J}, \Pred,  
 				\Post}
-			{\ostate{s_i^{i\in L}} \OTarrow {v}
+			{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
 				\ostate{s_i'^{\, i\in L}}}
@@
 			{
-				\{{\beta_j}\}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
+				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
 				\Pred\,',  
 				\Post\,'}
-			{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {v}
+			{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {\alpha}
 				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
@@
 			{
-				\{\xrightarrow{\beta_j}\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
+				\beta_j^{j\in J\cap\Holes(Q)}, \Pred\,'',  
 				\Post\,''}
-			{\ostate{s_i^{i\in L_Q}} \OTarrow {v_Q}
+			{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
 				\ostate{s_i'^{\,i\in L_Q}}}
@@
 		\end{mathpar}
-		and  $\Pred\subst{v_Q\leftarrow \beta_{j_0}} =(\Pred\,'
-		\land \Pred\,'')$, $\Post=\Post\,'\uplus 
+		and  $\Pred \iff \Pred\,'
+		\land \Pred\,''\land \alpha_Q=\beta_{j_0}$, $\Post=\Post\,'\uplus 
 		\Post\,''$ where $\Post\,''$ is the restriction of $\Post$ over variables of 
@@
     	{
-    	\{{\beta_{j}}\}^{j\in J_m}, \Pred_m, \Post_m}
-    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
+    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
+    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
     		\ostate{(s_i^\prime)^{i\in L_m}}}\]
@@
     	{\emptyset, \Pred_m, \Post_m}
-    	{\ostate{s_m} \OTarrow {v_m}
+    	{\ostate{s_m} \OTarrow {\alpha_m}
     		\ostate{s_m'}}}\]
@@
 		{
-			\{{\beta_j}\}^{j\in J\cap\Holes(Q)}, \Pred_{j_0},  
+			\beta_j^{j\in J\cap\Holes(Q)}, \Pred_{j_0},  
 			\Post\,''}
-		{\ostate{s_i^{i\in L_Q}} \OTarrow {v_{j_0}}
+		{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_{j_0}}
 			\ostate{(s_i')^{\, i\in L_Q}}}
@@
 if we 
-choose\footnotemark[\thefootnote]  $v_Q=v_{j_0}$ ($\Pred\,''= \Pred_{j_0}$). Considering 
+choose\footnotemark[\thefootnote]  $\alpha_Q=\alpha_{j_0}$ and $\Pred\,''= \Pred_{j_0}$. 
+Considering 
 the OT of $P$ we have  $I'_P=I'\setminus L_Q$, and $J'_P=J'\setminus\Holes(Q)\uplus 
 \{j_0\}$;  the predicate is 
-$\Pred\,'=\bigwedge_{m\in I_k}\Pred_m  \land \Pred_{\symb{sv}}(SV_k,v_m^{m\in 
-I},\beta_j^{j\in J\cup \{j_0\}},v)$
-where\footnotemark[\thefootnote] $\Pred_{\symb{sv}}(SV_k,v_m^{m\in I},\beta_j^{j\in J\cup 
-\{j_0\}},v)\Leftrightarrow 
-\forall i\in I_k.\, \alpha_i=a_i\land \forall j \in J\cup \{j_0\}.\, \alpha_j=\beta_j 
+$\Pred\,'=\bigwedge_{m\in I_k}\Pred_m  \land \Pred_{\symb{sv}}(SV_k,\alpha_m^{m\in 
+I},\beta_j^{j\in J\cup \{j_0\}},\alpha)$
+where\footnotemark[\thefootnote] $\Pred_{\symb{sv}}(SV_k,\alpha_m^{m\in I},\beta_j^{j\in 
+J\cup 
+\{j_0\}},\alpha)\Leftrightarrow 
+\forall i\in I_k.\, \alpha_i=\alpha'_i\land \forall j \in J\cup \{j_0\}.\, 
+\beta_j=\alpha'_j 
 \land 
-v=\alpha'
+\alpha=\alpha'
 \land e_b$. Modulo renaming of fresh variables, this is identical to the predicate that 
 occurs in 
-the source open transition except $\alpha_{j_0}=v_{j_0}$ has been replaced by  
-$\alpha_{j_0}=\beta_{j_0}$.
-Thus, $\Pred\subst{v_Q\leftarrow \beta_{j_0}}=(\Pred\,' 
-\land \Pred\,'')$. %\TODO{the argument on renaming has mostly been
-                 %removed is it still OK? yes.}. 
+the source open transition except $\alpha_{j_0}=\alpha'_{j_0}$ has been replaced by  
+$\beta_{j_0}=\alpha'_{j_0}$. As $\alpha_{j_0}=\alpha_Q$ and $\beta_{j_0}$ is free, we 
+have $\beta_{j_0}=\alpha'_{j_0}\land \beta_{j_0}=\alpha_Q \iff 
+\alpha_{j_0}=\alpha'_{j_0}$.
+Thus, $\Pred \iff (\Pred\,'
+		\land \Pred\,'')\land \alpha_Q=\beta_{j_0}$. 
 Finally, Post 
@@
 	{
-		\{{\beta_j}\}^{j\in J}, 
+		\beta_j^{j\in J}, 
 		\Pred,  
 		\Post}
-	{\ostate{s_i^{i\in L}} \OTarrow {v}
+	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
 		\ostate{s_i'^{\, i\in L}}}
@@
 	{
-		\{{\beta_j}\}^{j\in J_Q},
+		\beta_j^{j\in J_Q},
 		 \Pred\,',  
 		\Post\,'}
-	{\ostate{s_i^{i\in L_Q}} \OTarrow {v_Q}
+	{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
 		\ostate{s_i'^{\, i\in L_Q}}}
@@
 		{
-			\{{\beta_j}\}^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
-			\Pred\land\Pred\,'\subst{\beta_{j_0}\leftarrow v_Q},  
+			\beta_j^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
+			\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0},  
 			\Post\uplus \Post\,'}
-		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {v}
+		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {\alpha}
 			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
@@
 Note that this does not mean that any two pNets can be composed and produce an open 
-transition. Indeed, the predicate $\Pred\,'\subst{\beta_{j_0}\leftarrow v_Q}$ might not 
-be satisfiable if the open transition of $Q$ cannot be matched with $\beta_{j_0}$.
-
-\LUDO{Question/comment: this formulation makes the proof easy and supposes that we use 
-enough 
-variables, which is in accordance with the implementation and the way we define SV, but I 
-believe that $\Pred\,'\land \beta_{j_0}= v_Q$ might be better because more flexible and 
-less dependant of the way OTs are defined}
-
+transition. Indeed, the predicate $\Pred\land\Pred\land \alpha_Q=\beta_{j_0}$ is not 
+be satisfiable if the action of $\alpha_Q$ cannot be matched with $\beta_{j_0}$.
+Note also that $\beta_{j_0}$ is now only used as an intermediate term inside formulas: it 
+does not appear neither as global action nor as an action of a hole.
 \begin{small}
@@
 $K$ and the synchronisation vector are unchanged ($j_0$ is now in the set of sub-pNets); 
-$SV_k=\SV{\alpha_j^{j\in I\uplus\{j_0\}\uplus 
+$SV_k=\SV{(\alpha'_j)^{j\in I\uplus\{j_0\}\uplus 
 	J}}{\alpha'}{e_b}$. $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$. $I$ and $J$ 
@@
     	{\emptyset, \Pred_m, \Post_m}
-    	{\ostate{s_m} \OTarrow {v_m}
+    	{\ostate{s_m} \OTarrow {\alpha_m}
     		\ostate{s_m'}} }\]
@@
 transition is: $\Pred\,''=\bigwedge_{m\in I _1\uplus I_2}\Pred_m \land \Pred\,'
-\land \Pred(SV_k,v_i^{i\in I_1\uplus I_2}\uplus(j_0\mapsto v_Q),\beta_j^{j\in J},v)$. By 
-definition 
-$\Pred(SV_k,a_i^{i\in I}\uplus(j_0\mapsto v_Q),\beta_j^{j\in J},v)\Leftrightarrow
-	\forall i\in I.\, a_i=\alpha_i\land \forall j \in J.\, \beta_j=\alpha_j \land 
-	\alpha'_k=v\land v_Q=\alpha_{j_0}\land e_b$, finally 
-	$\Pred\,''=\Pred\subst{\beta_{j_0}\leftarrow 
-	v_Q} \land \Pred\,'$. The post-condition gathers the post-conditions related to all 
+\land \Pred(SV_k,v_i^{i\in I_1\uplus I_2}\uplus(j_0\mapsto v_Q),\beta_j^{j\in 
+J},\alpha)$. 
+By definition 
+$\Pred(SV_k,\alpha_i^{i\in I}\uplus(j_0\mapsto \alpha_Q),\beta_j^{j\in 
+J},v)\Leftrightarrow
+	\forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, \beta_j=\alpha'_j \land 
+	\alpha=\alpha'\land \alpha_Q=\alpha_{j_0}\land e_b$,
+this is equivalent to $\forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, 
+\beta_j=\alpha'_j \land 
+	\alpha=\alpha'\land \alpha_Q=\beta_{j_0}\land \beta_{j_0}=\alpha_{j_0}\land e_b$
+ and by definition of $\Pred$ (as obtained by \textbf{Tr2}),
+	$\Pred\,''\iff \Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0}$. The post-condition 
+	gathers the post-conditions related to all 
 	the leaves. Finally, the composed open transition can be
@@
  {
- 	\{{\beta_j}\}^{j\in J},\Pred_{OT},\Post_{OT}}
- { \ostate{s_{i}^{i \in L_P\uplus L}}\OTarrow {v} \ostate{{s'}_{i}^{~i \in 
+ 	\beta_j^{j\in J},\Pred_{OT},\Post_{OT}}
+ { \ostate{s_{i}^{i \in L_P\uplus L}}\OTarrow {\alpha} \ostate{{s'}_{i}^{~i \in 
  			L_P\uplus 
@@
  	{
- 		\{{\beta_j}\}^{j\in J'}, 
+ 		\beta_j^{j\in J'}, 
  		\Pred\,',  
  		\Post\,'}
- 	{\ostate{s_{i}^{i\in L_P}} \OTarrow {v}
+ 	{\ostate{s_{i}^{i\in L_P}} \OTarrow {\alpha}
  		\ostate{s_{i}'^{\,i\in L_P}}}
@@
  	{
- 		\{\xrightarrow{\beta_j}\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
+ 		\beta_j^{j\in J\cap\Holes(Q)}, \Pred\,'',  
  		\Post\,''}
- 	{\ostate{s_{i}^{i\in L}} \OTarrow {v_Q}
+ 	{\ostate{s_{i}^{i\in L}} \OTarrow {\alpha_Q}
  		\ostate{s_{i}'^{\,i\in L}}}
  }\end{mathpar}
- and  $\Pred_{OT}\subst{v_Q\leftarrow \beta_{j_0}} =({\Pred\,'}
- \land {\Pred\,}'')$, $\Post_{OT}=\Post\,'\uplus 
+ and  $\Pred_{OT}\iff \Pred\,'
+ \land \Pred\,''\land \alpha_Q= \beta_{j_0}$, $\Post_{OT}=\Post\,'\uplus 
  \Post\,''$ ($\Post\,''$ is the restriction of $\Post$ over variables of 
@@
  {
- 	\{\beta_{j x}\}^{j\in J\cap\Holes(Q)}, 
+ 	\beta_{j x}^{j\in J\cap\Holes(Q)}, 
  	\Pred_{OT_x},\Post_{OT_x}}
- {\ostate{t_{i}^{i\in L'}} \OTarrow {v_x} \ostate{t_{i x}^{i\in L'}}}
+ {\ostate{t_{i}^{i\in L'}} \OTarrow {\alpha_x} \ostate{t_{i x}^{i\in L'}}}
  \end{mathpar}
@@
  and  \\
- $\Pred \land \Pred\,''
+ $\Pred_{s,t} \land \Pred\,''
  \Rightarrow \bigvee_{x\in X}
@@
  \Pred_{OT_x}
- \land v_Q\!=\!v_x \land  
+ \land \alpha_Q\!=\!\alpha_x \land  
  \Pred_{s x}\subst{\Post\,''}\subst{\Post_{OT_x}}\right)$
@@
  	{
- 		\{{\beta_{j x}}\}^{j\in J}, 
- 		\Pred\,'\subst{\beta_{j_0 x}\leftarrow v_x}\land\Pred_{OT_x},  
+ 		\beta_{j x}^{j\in J}, 
+ 		\Pred\,'\land\Pred_{OT_x}\land \alpha_x=\beta_{j_0 x} ,  
  		\Post\,'\uplus \Post_{OT_x} }
- 	{\ostate{t_{i }^{i\in L'\uplus L_Q}} \OTarrow {v_x}
+ 	{\ostate{t_{i }^{i\in L'\uplus L_Q}} \OTarrow {\alpha_x}
  		\ostate{{t}_{i x}^{i\in L'\uplus L_Q}}}
@@
  \mathcal{R}'$ (by definition of
- $\mathcal{R}'$) and in four steps we get:
+ $\mathcal{R}'$) and in three steps we get:
 
@@
  \begin{small} $\Pred_{s,t} \land \Pred_{OT} \implies
- 	\Pred_{s,t}\land(\Pred\,'\land \Pred\,'')\subst{\beta_{j_0}\leftarrow v_Q}\\ % 
+ 	\Pred_{s,t}\land\Pred\,'\land \Pred\,''\land\alpha_Q=\beta_{j_0}\\ % 
  	%reversed 
  	%substitution 
- 	\implies 
- 	(\Pred_{s,t}\land\Pred\,'')\land \Pred\,'\subst{\beta_{j_0}\leftarrow v_Q}\\ % 
- 	%$b_{j_0}$ 
- 	%only 
- 	%appears 
- 	%in $\Pred\,'$
  	\implies  \hspace{-2ex}
@@
  	\Pred_{OT_x}
- 	\land v_Q\!=\!v_x \land  
+ 	\land \alpha_Q\!=\!\alpha_x \land  
  	\Pred_{s x}\subst{\Post\,''}\subst{\Post_{OT_x}}\right)
  }
- \\~\qquad\qquad	\land \Pred\,'\subst{\beta_{j_0}\leftarrow v_Q} \\
+ \\~\qquad\qquad	\land \Pred\,'\land\alpha_Q=\beta_{j_0} \\
  	\implies
@@
  		\left( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \Rightarrow 
- 		\Pred\,'\subst{\beta_{j_0}\leftarrow v_x}\land \Pred_{OT_x}
- 		\land v_Q\!=\!v_x \land  
+ 		\Pred\,'\land \Pred_{OT_x}
+ 		\land \alpha_Q\!=\!\alpha_x \land \alpha_Q\!=\!\beta_{j_0 x} \land  
  		\Pred_{s x}\subst{\Post\,''}\subst{\Post_{OT_x}}\right)
@@
  	$\end{small}
-
+ Note that, $\beta_{j_0}$ can be transformed into  $\beta_{j_0 x}$ because of the 
+ implication hypothesis.
  %\TODO{There was a confusion between the $\Rightarrow$ between the
  %  steps, and the $\implies$ inside the formulas...}
-
- Explanations: first, we reversed the substitution; then we
- restricted the 
- substitution as $\beta_{j_0}$ only appears in $\Pred\,'$; then we
- applied the property of FH-bisimulation for $P$ and rearranged the
- terms using the fact that $v_Q=v_x$. The obtained formula reaches the goal except for 
+% 
+% Explanations: first, we reversed the substitution; then we
+% restricted the 
+% substitution as $\beta_{j_0}$ only appears in $\Pred\,'$; then we
+% applied the property of FH-bisimulation for $P$ and rearranged the
+% terms using the fact that $v_Q=v_x$.
+ The obtained formula reaches the goal except for 
  two points:\\[-4.3ex] 
@@
  \end{itemize}	
+Finally: 
+\[{\displaystyle\bigvee_{x\in X}
+ 		\left( \forall j\in J. \beta_j=\beta_{jx}  \Rightarrow 
+ 		\left(\Pred\,'\land \Pred_{OT_x}
+ 		 \land \alpha_Q\!=\!\beta_{j_0 x}\right) \land \alpha_Q\!=\!\alpha_x\land  
+ 		\Pred_{s x}\subst{\Post\,''}\subst{\Post_{OT_x}}\right)
+ 	}\]
  This proves the  condition of the FH-simulation, the other direction is 
@@
 	{
-		\{{\beta_j}\}^{j\in J},\Pred_{OT},\Post_{OT}}
-	{ \ostate{s_{i}^{i \in L\uplus L_Q}}\OTarrow {v} \ostate{{s'}_{i}^{~i \in 
+		\beta_j^{j\in J},\Pred_{OT},\Post_{OT}}
+	{ \ostate{s_{i}^{i \in L\uplus L_Q}}\OTarrow {\alpha} \ostate{{s'}_{i}^{~i \in 
 	L\uplus 
@@
 				{
-					\{{\beta_j}\}^{j\in J'}, 
+					\beta_j^{j\in J'}, 
 					\Pred\,',  
 					\Post\,'}
-				{\ostate{s_{1}^{i\in L}} \OTarrow {v}
+				{\ostate{s_{1}^{i\in L}} \OTarrow {\alpha}
 					\ostate{s_{i}'^{~ i\in L}}}
@@
 				{
-					\{{\beta_j}\}^{j\in J\cap\Holes(Q)}, \Pred\,'',  
+					\beta_j^{j\in J\cap\Holes(Q)}, \Pred\,'',  
 					\Post\,''}
-				{\ostate{s_{i}^{i\in L_Q}} \OTarrow {v_Q}
+				{\ostate{s_{i}^{i\in L_Q}} \OTarrow {\alpha_Q}
 					\ostate{s_{i}'^{~ i\in L_Q}}}
 			}\end{mathpar}
-			and  $\Pred_{OT}\subst{v_Q\leftarrow \beta_{j_0}} =({\Pred\,}'
-			\land {\Pred\,}'')$, $\Post_{OT}=\Post\,'\uplus 
+			and  $\Pred_{OT} \iff \Pred\,'
+		\land \Pred\,''\land \alpha_Q=\beta_{j_0}$, $\Post_{OT}=\Post\,'\uplus 
 			\Post\,''$ ($\Post\,''$ is the restriction of $\Post$ over variables of 
@@
 			{
-				\{{\beta_{j x}}\}^{j\in J'}, 
+				\beta_{j x}^{j\in J'}, 
 				\Pred_{OT_x},\Post_{OT_x}}
-			{\ostate{t_{i}^{i\in L'}} \OTarrow {v_x} \ostate{t_{i x}^{i\in L'}}}
+			{\ostate{t_{i}^{i\in L'}} \OTarrow {\alpha_x} \ostate{t_{i x}^{i\in L'}}}
 			%         \right)
@@
 		 \Rightarrow \bigvee_{x\in X}
-			\left( \forall j\in J'. b_j=b_{jx}  \Rightarrow 
+			\left( \forall j\in J'. \beta_j=\beta_{jx}  \Rightarrow 
 			\Pred_{OT_x}
-			\land v\!=\!v_x \land  
+			\land \alpha\!=\!\alpha_x \land  
 			\Pred_{s x}\subst{\Post\,'}\subst{\Post_{OT_x}}\right)$
@@
 					{
-						\{{b_{j x}}\}^{j\in J}, 
-						\Pred_{OT_x}\subst{b_{j_0 x}\leftarrow v_Q}\land\Pred\,'',  
+						\beta_{j x}^{j\in J}, 
+						\Pred_{OT_x} \land\Pred\,''\land\alpha_Q=\beta_{j_0 x},  
 						\Post_{OT_x}\uplus \Post\,''}
-					{\ostate{t_{ i }^{i\in L'\uplus L_Q}} \OTarrow {v_x}
+					{\ostate{t_{ i }^{i\in L'\uplus L_Q}} \OTarrow {\alpha_x}
 						\ostate{{t}_{ i x}^{i\in L'\uplus L_Q}}}
@@
 \begin{small} $\Pred_{s,t} \land \Pred_{OT} \implies
- \Pred_{s,t}\land(\Pred\,'\land \Pred\,'')\subst{b_{j_0}\leftarrow v_Q}\\ % reversed 
- %substitution 
- \implies 
- (\Pred\land\Pred\,')\subst{b_{j_0}\leftarrow v_Q}\land \Pred\,''\\ % $b_{j_0}$ only 
- %appears 
- %in $\Pred\,'$
+ \Pred_{s,t}\land\Pred\,'\land \Pred\,''\land \alpha_Q=\beta_{j_0}\\  
  \implies  \hspace{-2ex}
-{\displaystyle{\bigvee_{x\in X}\!(\forall j\!\in\! J'. b_j\!=\!b_{jx}  
+{\displaystyle{\bigvee_{x\in X}\!(\forall j\!\in\! J'. \beta_j\!=\!\beta_{jx}  
 \Rightarrow \!
-\Pred_{OT_x}\subst{b_{j_0}\!\!\leftarrow\!\! v_Q}
-\land v\!=\!v_x}} %\\ \hspace*{40mm} %
+\Pred_{OT_x}\land \alpha_Q=\beta_{j_0}
+\land \alpha\!=\!\alpha_x}} %\\ \hspace*{40mm} %
 \land \Pred_{s x}\subst{\Post\,'}\subst{\Post_{OT_x}}) \land
@@
  \implies  \hspace{-2ex}
- {\displaystyle{\bigvee_{x\in X}\!( \forall j\!\in\! J'. b_j\!=\!b_{jx} \Rightarrow 
-\Pred_{OT_x}\subst{b_{j_0}\!\!\leftarrow\!\! v_Q}\!\land\! \Pred\,''%\\ \hspace*{40mm}
-\!\land\! v\!=\!v_x \!\land\!  
-\Pred_{s x}\subst{\Post\,'}\subst{\Post_{OT_x}})}} 			
+	{\displaystyle{\bigvee_{x\in X}\!(\forall j\!\in\! J'. \beta_j\!=\!\beta_{jx}  
+\Rightarrow \!
+\left(\Pred_{OT_x}\land
+\Pred\,''
+\land \alpha_Q=\beta_{j_0 x}\right)
+\land \alpha\!=\!\alpha_x}} 
+\land \Pred_{s x}\subst{\Post\,'}\subst{\Post_{OT_x}}) 	
 $\end{small}
@@
 
-Explanations: first, we reversed the substitution; then we
-restricted the 
-substitution as $b_{j_0}$ only appears in $\Pred\,'$; then we
-applied the property of FH-bisimulation for $P$ and rearranged the
-terms. The obtained formula reaches the goal except for two points:\\[-4.3ex] 
+ The obtained formula reaches the goal except for two points:\\[-4.3ex] 
 \begin{itemize}

### 2018-04-20 2017-Xudong-SMT/AVOCS-2018.tex

@@
 $\mathcal{A}_\P$, with $\mathcal{A}_P\subseteq\mathcal{T}_\P,
-\mathcal{E}_P\cap\mathcal{A}_P=\emptyset$;
+\mathcal{E}_\P\cap\mathcal{A}_\P=\emptyset$;
 naturally action terms will use data expressions as sub-terms.
@@
 In practice, the parameterization of the pNet model by some specific
-action algebra is realized by the definition of an ``algebra
+action algebra is realized by the definition of an many-sorted ``algebra
 presentation''. It will be used to check the
@@
   \begin{itemize}
-  \item $Sorts$ is a set of \emph{sorts}
+  \item $Sorts$ is a set of data \emph{sorts}
     % \noteSB{Commented out a footnote here\mdash check if still necessary.}
@@
 Now, we define
-pNet nodes as constructors for hierarchical behavioural structures.
+pNet nodes as constructors for hierarchical structures.
 A pNet node has a set of sub-pNets that can be either pNets or pLTSs, and a
-set of \emph{holes}, playing the role of process parameters.
+set of \emph{holes}, playing the role of process parameters
+(i.e. unknown in the environment).
 
@@
 \cite{henrio:Forte2016}, in the form of 2 structural rules, one for
-pLTSs, one for pNet nodes.  For convenience we include these rules in
+pLTSs, one for pNet nodes.  For convenience we also include these rules in
 App.~\ref{appendix:semRules}.
@@
 computes all possible OTs, adding their target states in the
-unexplored set, until this set is empty. As the potential set of
-global states is finite (see \cite{henrio:Forte2016}), this terminates.
+unexplored set, until this set is empty. As the set of
+global states is finite (under the conditions above), this terminates.
 

### 2018-04-23 2017-Xudong-SMT/AVOCS-2018.tex

@@
 that we use here for satisfiability of open transitions will be
-similar with what we need to prove (symbolic) equivalence between open
+similar with what we need when proving (symbolic) equivalence between open
 transitions.
@@
     industry-inspired case-study, namely one architectural pattern
-    extracted from the BIP specification of a nanosatellite on-board
+    extracted (and extended) from the BIP specification of a nanosatellite on-board
     software.
@@
 
+BIP
+(Behaviour-Interaction-Priority)~\cite{bip} is a framework for the
+component-based design of concurrent software and systems.  In
+particular, the BIP tool-set comprises compilers for generating C/C++
+code, executable by linking with one of the dedicated engines, which
+implement the BIP operational semantics~\cite{BarBliu15-offer-scico}.  This
+approach ensures that any property, shown to hold on a given BIP
+model, will also hold by construction on the generated code.
+BIP Architectures~\cite{AttieBBJS16-architectures-faoc} formalise
+design patterns, which enforce global properties 
+characterising the coordination among the components of the
+system. They provide a compositional approach, ensuring
+correctness by construction during the design of BIP models.
+In~\cite{AttieBBJS16-architectures-faoc}, it was shown that
+application of architectures is compositional \wrt safety properties,
+\ie when several architectures are applied, each enforcing a safety
+property, the resulting system satisfies their conjunction.
+
+But the interaction feature in architectures does not handle
+data-sensitive interaction constraints. Using an encoding of
+architectures, extended with data-dependant interactions, into open
+pNets was an interesting alternative to a direct extension to the
+architecture semantics.
+
 \paragraph{Structure.}
@@
 On top of $\mathcal{E}_\P$ we build the action algebra
-$\mathcal{A}_\P$, with $\mathcal{A}_P\subseteq\mathcal{T}_\P,
+$\mathcal{A}_\P$, with $\mathcal{A}_\P\subseteq\mathcal{T}_\P,
 \mathcal{E}_\P\cap\mathcal{A}_\P=\emptyset$;
@@
 CubETH nanosatellite on-board software
-case-study~\cite{CubETH-case-study} realised using BIP.  BIP
-(Behaviour-Interaction-Priority)~\cite{bip} is a framework for the
-component-based design of concurrent software and systems.  In
-particular, the BIP tool-set comprises compilers for generating C/C++
-code, executable by linking with one of the dedicated engines, which
-implement the BIP operational semantics~\cite{BarBliu15-offer-scico}.  This
-approach ensures that any property, shown to hold on a given BIP
-model, will also hold by construction on the generated code.
-
-In this context, the notion of \emph{architecture} was proposed
-in~\cite{AttieBBJS16-architectures-faoc} as a mechanism for ensuring
-correctness by construction during the design of BIP models.
-Architectures can be viewed as operators transforming BIP models.
-They formalise design patterns, which enforce global properties
-characterising the coordination among the components of the system.
+case-study~\cite{CubETH-case-study} realised using BIP.
 The architecture-based design process in BIP takes as input a set of
@@
 temporal properties that must be enforced in the final system.  For
-each property, a corresponding architecture is identified\,\footnote{%
-%
-  The current approach relies on taxonomies of predefined
-  architectures.  Future work may include automatic synthesis of
-  architectures from, \eg CTL~\cite{BaierKatoen2008} formulae.
-%
-} and applied to the model, thereby potentially introducing additional
+each property, a corresponding architecture is identified
+%\,\footnote{%
+%
+%  The current approach relies on taxonomies of predefined
+%  architectures.  Future work may include automatic synthesis of
+%  architectures from, \eg CTL~\cite{BaierKatoen2008} formulae.
+%
+  %}
+  and applied to the model, thereby potentially introducing additional
 coordinator components and modifying the connectors that define
 synchronisation patterns among ports of components.
-In~\cite{AttieBBJS16-architectures-faoc}, it was shown that
-application of architectures is compositional \wrt safety properties,
-\ie when several architectures are applied, each enforcing a safety
-property, the resulting system satisfies their conjunction.
 
@@
 synchronisation vectors, and with finite pLTSs, has a finite
-semantics. But all the elements of such pNets and open automata being
+semantics. Remark that all the elements of such pNets and open automata being
 symbolic, they can represent many classes of unbounded systems.
@@
 apply only the simplest filter inside the \emph{Matching} method
-(before applying the predicate and OT construction). All
-the rest will be checked later, using the satisfiability check in the
-SMT engine.
+(before applying the predicate and OT construction). Matching and
+unification  will be checked later, together with the guards collected
+from synchronisation vectors and from pLTS transtions, using the
+satisfiability check in the SMT engine.
 
@@
 variables (which may be used in a transition) %% will simply be
-the union
+is the disjoint union
 of sets of state variables of the individual pLTS states constituting this
-global state (variables of different pLTS are distinct).
+global state.
 %There are some assignment on the variables in each of states of the pLTS (state variables), or just as global states of it (global variables).
@@
 names from our example.
+Additionally, we will include axiomatisation of any required functions
+and predicates of the presentation data-types.
 
@@
 
-\emph{Translation of open transitions}
-
+\emph{Translation of open transitions.}
 In App.~\ref{appendix:mapsmt} we formally define all steps of the translation of each
@@
 %
-Here again, this translation ensures that no runtime error will occur
-when running the SMT engine.
+This translation ensures that no runtime error will occur
+in the SMT engine.
 
@@
 inequality, or a guard. 
-The result (sat or unsat) of the final command in the translation (\texttt{check-sat}) is decoded by
-)our algorithm.
+The result (sat or unsat) of the final \texttt{check-sat} command in
+the translation () is then decoded.
 
@@
 will be to model-check logical properties, and to check equivalence of pNets. While
-model-checking open automata (with a suitable logic including
-predicates on data) seems easy to define, equivalence checking is more challenging.
+model-checking open automata  seems easy to define, equivalence
+checking is more challenging. 
 In~\cite{henrio:Forte2016}, we
-have already found the FH-bisimulation, inspired by~\cite{deSimone85}, to be a
+have already found the FH-bisimulation, %inspired
+%by~\cite{deSimone85},
+to be a
 suitable definition. But weak equivalences, or refinements, will
@@
 attack the complexity of verification of realistic systems by a
-composition and parametric approach. Still one may wonder if the price
+compositional and parametric approach. Still one may wonder if the price
 for analysing our our symbolic transitions will not make the approach
-innaplicable. As a first exercice in this direction, we tried a
-slighly bigger example, assembling 2 Failure controlers. We give some
-figures from this try in appendix~\ref{appendix:scalingup}, showing that Z3 can check the
-satisfiablility of a 90K open transitions in a metter of minutes.
+inapplicable. Here we tried a
+slighly bigger example, assembling 2 Failure controlers. In
+appendix~\ref{appendix:scalingup}, we show that Z3 can check the
+satisfiablility of a 90K open transitions in a couple of minutes.
 
@@
 
-These are organized in the following way:
+The appendices are organized in the following way:
 

### 2018-04-23 2016-Weak-FH-Bisim/WeakBisim.tex
weak OT page 14

--- 2018-04-19 2016-Weak-FH-Bisim/WeakBisim.tex
@@
   \label{OT:ABP}
+At the upper level, the $ABP$ pNet has 2 holes and and $Protocol$ has
+a subnet. One of its possible transition (synchronizing the hole $P$
+with the $Protocol$) is:
+
+ \smallskip\noindent
+ $  OT_1  = \openrule{
+%                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
+%                            \xrightarrow{in(?m,?b)}_{M1}
+      (P\mapsto send(m)); Pred=[m=m']; Post=\{s1\_m:=m\}
+                      }
+  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
+    {\ostate{s_0,m_0,m_0,r_0} \OTarrow{\underline{send(m')}} \ostate{s_1,m_0,m_0,r_0}}
+    $
+
+    \smallskip
+    The global states here have the same structure than
+    in $OT\_2$, as the holes have no states. The assignment
+    $Post$ uses a variable from the action of hole $P$ to set the
+    value of the sender state variable $s1\_m$.
+
   The \texttt{Protocol} pNet of Fig. \ref{schema:ABP-composed} has 4 controllers and no holes. One of its possible open-transition (the sender sending $(m,b)$ to the medium) is:
@@
    %                           \xrightarrow{in(?m,?b)}_{M1}
-      \emptyset; Pred=[m=s_1\_m, b=s_1\_sb];  Post=\{m_1\_m:=m, m_1\_b:=b\}
+   \emptyset; Pred=[send(SV2\_m, SV2\_b)=send(s_1\_m, s_1\_sb);in(SV2\_m, SV2\_b)=in(?m,?b)];  \\ Post=\{m_1\_m:=?m, m_1\_b:=?b, s_2\_sb:=s_1\_sb\}
                       }
   %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
-    {\ostate{s_1,m_0,m_0,r_0} \OTarrow{\tau} \ostate{s_2,m_1,m_0,r_0}}
+    {\ostate{s_1,m_0,m_0,r_0} \OTarrow{\underline{send(SV2\_m, SV2\_b)}} \ostate{s_2,m_1,m_0,r_0}}
+    $
+
+    \ERIC{Apres resolution de l'unification:}
+
+     $  OT_2  = \openrule{
+%                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
+   %                           \xrightarrow{in(?m,?b)}_{M1}
+      \emptyset; Pred=[s_1\_m=SV2\_m, SV2\_m=?m, s_1\_sb=SV2\_b, SV2\_b=?b];  \\ Post=\{m_1\_m:=?m, m_1\_b:=?b, s_2\_sb:=s_1\_sb\}
+                      }
+  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
+    {\ostate{s_1,m_0,m_0,r_0} \OTarrow{\underline{send(s_1\_m, s_1\_b)}} \ostate{s_2,m_1,m_0,r_0}}
+    $
+
+    \ERIC{Apres application des substitutions et simplification du predicat:}
+
+     $  OT_2  = \openrule{
+      \emptyset; Pred=true;  \\ Post=\{m_1\_m:=s_1\_m, m_1\_b:=s_1\_sb, s_2\_sb:=s_1\_sb\}
+                      }
+    {\ostate{s_1,m_0,m_0,r_0} \OTarrow{\underline{send(s_1\_m, s_1\_b)}} \ostate{s_2,m_1,m_0,r_0}}
     $
@@
     \smallskip
-At the upper level, the $ABP$ pNet has 2 holes and and $Protocol$ has
-a subnet. One of its possible transition (synchronizing the hole $P$
-with the $Protocol$) is:
-
- \smallskip\noindent
- $  OT_1  = \openrule{
-%                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
-%                            \xrightarrow{in(?m,?b)}_{M1}
-      (P\mapsto send(m)); Pred=[m=m']; Post=\{s1\_m:=m\}
-                      }
-  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
-    {\ostate{s_0,m_0,m_0,r_0} \OTarrow{\underline{send(m')}} \ostate{s_1,m_0,m_0,r_0}}
-    $
-
-    \smallskip
-    The global states here have the same structure than
-    in $OT\_2$, as the holes have no states. The assignment
-    $Post$ uses a variable from the action of hole $P$ to set the
-    value of the sender state variable $s1\_m$.
+
 \end{example}
@@
 pick all $\tau^*$ and $\tau^*;a;\tau^*$ sequences from the OA, and build a weak
-OT from each sequence. Here is one example:
+OT from each sequence. Here is one example of a short sequence,
+starting with the open transition $OT_2$ of page \pageref{OT:ABP},
+then transmitting the message to the receiver (if the sender and
+receiver control bits are equal), and to the environnement. The two
+firts OTs are internal, the last one is visible, so it constitute a
+$\tau;\tau;a$ weak transition.
 
 \noindent
-$\ostate{1000}\OTarrow{m\_rec(m,x), \phi_1 = [x=s_1\_b \land
+     $  \openrule{
+      \emptyset; Pred=true; Post=\{m_1\_m:=s_1\_m, m_1\_b:=s_1\_sb, s_2\_sb:=s_1\_sb\}
+                      }
+    {\ostate{s_1,m_0,m_0,r_0} \OTarrow{\underline{send(s_1\_m, s_1\_b)}} \ostate{s_2,m_1,m_0,r_0}}
+    $
+
+\medskip\noindent
+     $  \openrule{
+      \emptyset; Pred=[r_0\_rb=?b' \land ?m'=m_1\_m \land ?b=m_1\_b \land SV3\_m=?m' \land SV3\_b=?b'];
+      \\ Post=\{r_1\_rb:=r_0\_rb; r_1\_m:=?m'; r_1\_b:=?b'      \}
+                      }
+    {\ostate{s_2,m_1,m_0,r_0} \OTarrow{\underline{recv(SV3\_m, SV3\_b)}} \ostate{s_2,m_0,m_0,r_1}}
+    $
+
+    \ERIC{Apres simplification:}
+\medskip\noindent
+     $  \openrule{
+      \emptyset; Pred=[r_0\_rb=m_1\_b];
+      \\ Post=\{r_1\_rb:=r_0\_rb; r_1\_m:=m_1\_m; r_1\_b:=m_1\_b      \}
+                      }
+    {\ostate{s_2,m_1,m_0,r_0} \OTarrow{\underline{recv(m_1\_m,m_1\_b)}} \ostate{s_2,m_0,m_0,r_1}}
+    $
+    \\
+
+\medskip\noindent
+     $  \openrule{
+  \emptyset; Pred=true; Post=r_2\_b:=r_1\_b; s_2\_b:=s_1\_b   \}
+                      }
+    {\ostate{s_2,m_0,m_0,r_1} \OTarrow{out(r_1\_m)} \ostate{s_2,m_0,m_0,r_2}}
+    $
+    \\
+
+    \bigskip
+    \ERIC{Anciennes versions:}
+$\ostate{1000}\OTarrow{\underline{send(m,b)}, \phi_1 = [x=s_1\_b \land
     m=s_1\_m]}\ostate{2100}$\\
@@
  \noindent
- $$\ostate{1000}\OTWeakarrow{v,
-   [v=out(s_1\_m)\land r_0\_b=s_1\_b],\{r_2\_b:=r_0\_b\}} \ostate{2002}$$
+ $$ \openrule{
+   \emptyset; Pred=[r_0\_b=s_1\_b]; Post= \{r_2\_b:=r_0\_b  \}
+   }
+   {\ostate{s_1,m_0,m_0,r_0}\OTWeakarrow{out(s_1\_m)} \ostate{s_2,m_0,m_0,r_2}}$$
 %% \\

### 2018-04-23 2018-Arch-pNets/arch-pNets.tex
removed a comment
Brought in the figure from the SMT paper
Action labels in OTs

@@
     \begin{aligned}
-      \exists \bigl(q^1_C \goesto{b_1 \cap P_C, g^{b_1}_C, e^{b_1}_C}\bigr)^{C \in \supp{b_1} \cap \cC_1}:
+      \exists \bigl(q^1_C \goesto{b_1 \cap P_C, g^{b_1}_C, f^{b_1}_C}\bigr)^{C \in \supp{b_1} \cap \cC_1}:
       & \quad \left.
@@
             \left.
-            \exists \bigl(q^2_C \goesto{b_2 \cap P_C, g^{b_2}_C, e^{b_2}_C}\bigr)^{C \in \supp{b_2} \cap \cC_2}:
+            \exists \bigl(q^2_C \goesto{b_2 \cap P_C, g^{b_2}_C, f^{b_2}_C}\bigr)^{C \in \supp{b_2} \cap \cC_2}:
             h_2 \land
@@
 think last Expression should be removed not sure about the rest -- to be discussed}\noteSB{I agree: expressions are not needed, but it is nice to explain how action terms are formed }
-\removeSBin{def of $\AlgA$, $p_i$, $\Expr$}
+%\removeSBin{def of $\AlgA$, $p_i$, $\Expr$}
 %\[
@@
 	\inferrule*[myfraction=\reddottedrule]
-	{	\{\beta_j\}^{j\in J}, \Pred, \Post}
-	{s \OTarrow {v}s'}
+	{	\beta_j^{j\in J}, \Pred, \Post}
+	{s \OTarrow {{\alpha}}s'}
 	\end{mathpar}
@@
 	over the different variables of the
-	terms, labels, and states $s_i$, $\beta_j$, $s$, $v$. $\Post\in 
+	terms, labels, and states $s_i$, $\beta_j$, $s$, $\alpha$. $\Post\in 
 	\assigns{\variables}$\ is 
 	a set of assignments that are the effects of the transition.
-\noteSB{Why $v$? Why not $\alpha$? As now, it is not clear whether this is an action term 
-or a variable $v \in \vars(s)$ of some hypothetical state $s$.}\hl{$v$ is a variable 
-denoting the resulting action}
 \end{definition}
@@
                             0 \xrightarrow{l}_{C_4} 0  ~~  
-                            \xrightarrow{\delta(x4)}_P ~~
-                            \xrightarrow{accept(x4)}_Q 
+							(P\mapsto \delta(x4), Q\mapsto accept(x4))               
+%                            \xrightarrow{\delta(x4)}_P ~~
+%                            \xrightarrow{accept(x4)}_Q 
                       }
@@
 \end{example}
+
+It is important to understand the difference between the red dotted rule and a normal 
+inference rule. They correspond to two different logical levels.
+ The open transition is itself a logical implication, but using a simple logic (with the 
+ expressive power that is given to the predicate and necessary include logical 
+ propositions and equality). We differentiate classical (black) inference rules that use 
+ an expressive logic and are paper rules from open transition rules that use a simpler 
+ logic, 
+ will be embedded into automata transitions, and could typically be handled in a 
+ mechanical way.
 
@@
 \begin{multline}
-  \Pred_{\symb{sv}}(SV, 
-  \alpha_i^{i\in I}, \beta_j^{j\in J}, v)\Leftrightarrow
-  \\
-%\exists 
-%%   \bigg(
-%% \begin{array}{l}
-\exists {\vars((\alpha'_i)}^{i\in I}),
-{\vars((\beta'_j)}^{j\in J}),\vars(v').\, %SV=
-%\\
-%\land
-\\\forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, \beta_j=\beta'_j \land 
-v=v' \land g
-%% \end{array} \bigg)
-\\
-\text{ Where } SV=\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}}{ v'}{ g}
+\Pred_{\symb{sv}}(\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
+{\alpha'} {g}, \alpha_i^{i\in I}, \beta_j^{j\in J}, \alpha)\Leftrightarrow \\
+\forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, \beta_j=\beta'_j \land 
+\alpha=\alpha' 
+\land g
 \end{multline}
-\noteLH{Is and g sufficient? I would say yes}
-\noteSB{In principle, yes. I am not 100\% sure that the implicit dependency of $g$ on the variables in $a'_i$ and $b'_j$ is clear.}
 
@@
     	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
-k\!\in\! K \qquad SV_k \!=\! \SV{\alpha_m^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{g} \\
+k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
+\\
 \\     	
 	\forall m\!\!\in\!\! I_1. {\pNet_m 
-	\models\mprset{myfraction=\reddottedrule}\inferrule
+	\models\openrule
     	{
-    	\{{\beta_{j}}\}^{j\in J_m}, \Pred_m, \Post_m}
-    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
+    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
+    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
     		\ostate{(s_i^\prime)^{i\in L_m}}} }	
@@
     	 \models
-    	\mprset{myfraction=\reddottedrule}\inferrule
+    	\openrule
     	{\emptyset, \Pred_m, \Post_m}
-    	{\ostate{s_m} \OTarrow {v_m}
+    	{\ostate{s_m} \OTarrow {\alpha_m}
     		\ostate{s_m'}} }\\\\
@@
     	\models
-    	{\mprset{myfraction=\reddottedrule}\inferrule
+    	{\openrule
     		{
-    		\{{\beta_j}\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_1\uplus I_2} 
+    		{\beta_j}^{j\in J^\prime}, \Pred, \uplus_{m\in I_1\uplus I_2} 
     		\Post_m}
-    		{\ostate{s_i^{i\in L}} \OTarrow {v}
+    		{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
     			\ostate{(s_i^\prime)^{i\in L}}}

### 2018-04-23 2018-Arch-pNets/arch-pNets.tex
Imported the example from the SMT paper Extended with data -- only in the figure Text still to update

--- 2018-04-06 2018-Arch-pNets/arch-pNets.tex
@@
 \usepackage{hyperref}
+
+\input{figures/macros.tex}         % Definitions of macros used in XFig figures
 
@@
 \label{secn:introduction}
+
+BIP (Behaviour-Interaction-Priority)~\cite{bip} is a framework for the
+component-based design of concurrent software and systems.  In
+particular, the BIP tool-set comprises compilers for generating C/C++
+code, executable by linking with one of the dedicated engines, which
+implement the BIP operational semantics~\cite{BliSif08-acp-tc}.
+This approach ensures that any property, shown to hold on a given BIP
+model, will also hold by construction on the generated code.
+
+In this context, the notion of \emph{architecture} was proposed
+in~\cite{AttieBBJS16-architectures-faoc} as a mechanism for ensuring
+correctness by construction during the design of BIP models.
+Architectures can be viewed as operators transforming BIP models.
+They formalise design patterns, which enforce global properties
+characterising the coordination among the components of the system.
+The architecture-based design process in BIP takes as input a set of
+components providing basic functionality of the system and a set of
+temporal properties that must be enforced in the final system.  For
+each property, a corresponding architecture is identified
+%% \footnote{%
+%% %
+%%   The current approach relies on taxonomies of predefined
+%%   architectures.  Future work may include automatic synthesis of
+%%   architectures from, \eg CTL~\cite{BaierKatoen2008} formulae.
+%% %
+%% }
+and applied to the model, thereby potentially introducing additional
+coordinator components and modifying the connectors that define
+synchronisation patterns among ports of components.
+In~\cite{AttieBBJS16-architectures-faoc}, it was shown that
+application of architectures is compositional \wrt safety properties,
+\ie when several architectures are applied, each enforcing a safety
+property, the resulting system satisfies their conjunction.
+
+The concepts and results of the paper are illustrated by a running
+example extending the Failure Monitor architecture from the CubETH
+nanosatellite on-board software case-study~\cite{CubETH-case-study}.
 
@@
 %****************************************************************
-\subsection{Graphical representation of composed systems}
-\label{secn:connectors}
+\subsection{Running example: Failure Monitor architecture}
+\label{secn:failure-monitor}
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=\columnwidth]{BIPspec-ArchFailureTimerMax-v3}
+  \caption{The BIP specification of the Failure Monitor architecture}
+  \label{schema:ArchFailure:BIP}
+\end{figure}
+
+Figure~\ref{schema:ArchFailure:BIP} shows a refined version of the
+Failure Monitor architecture used in~\cite{CubETH-case-study}.
+Contrary to standard BIP models, architectures comprise one or several
+\emph{operand} components, whereof only the set of \emph{ports} is
+given.  Here, the operand component is $\NameOprnd$ and its interface
+consists of the ports $\PortFinish$, $\PortResume$ and $\PortFail$.
+The two \emph{coordinator} components\mdash $\NameCtrl$ and
+$\NameTimer$\mdash are standard BIP components insofar as they also
+have their \emph{behaviour} specified by finite automata extended with
+local data variables.  Transitions of these automata are labelled with
+the ports of the corresponding components, Boolean guards and update
+functions on local variables.  For instance the loop transition
+$\tstate{1} \goesto{\PortTick, \GuardTick[], \TimerUpd[]} \tstate{1}$
+in the $\NameTimer$ component is labeled by the port $\PortTick$, it
+can be fired only when the current value of the local variable $t$ is
+greater than $0$.  Upon firing, this transition decrements the value
+of $t$ by $1$.  When omitted, the default guard (\resp update
+function) is the constant predicate $\true$ (\resp the $\mathit{skip}$
+operator).  The constant $\mathrm{Max}$, in $\tstate{0}
+\goesto{\PortStart, \TimerInit[]} \tstate{1}$, is a parameter of the
+architecture.
+
+Connectors are hierarchical, tree-like structures with component ports
+at the leaves.  They define sets of \emph{interactions}, based on the
+attributes of the connected ports~\cite{BliSif08-acp-tc}, which may be
+either \emph{trigger} (triangles in Fig.~\ref{schema:ArchFailure:BIP})
+or \emph{synchron} (bullets in Fig.~\ref{schema:ArchFailure:BIP}).
+%
+If all sub-connectors of a connector are synchrons, then an
+interaction may be executed by the connector only if each subconnector
+can contribute.
+%
+If at least one of the sub-connectors is a trigger, then any
+interaction consisting of contributions of any set of sub-connectors,
+\emph{involving at least one of the triggers}, can be executed.
+%
+For instance, the two ports $\NameTimer.\PortStart$ and
+$\NameCtrl.\PortFail$ are always synchronised, since they belong to
+the same binary sub-connector, where they are both synchrons.  In
+particular, this means that whenever the transition $\cstate{0}
+\goesto{\PortFail} \cstate{1}$ is fired, so is the transition
+$\tstate{0} \goesto{\PortStart, \TimerInit[]} \tstate{1}$,
+initialising the timer.  The binary connector $\NameTimer.\PortStart
+\bullet\!\!\!-\!\!\!-\!\!\!\bullet \NameCtrl.\PortFail$ is a
+sub-connector of a hierarchical connector, where the port
+$\NameOprnd.\PortFail$ is a trigger.  Thus, the above interaction can
+only happen together with $\NameOprnd.\PortFail$, forming a
+ternary interaction.  On the contrary, being a trigger, the port
+$\NameOprnd.\PortFail$ can fire alone, forming a singleton
+interaction.  The composition semantics of BIP systems consists in
+firing exactly one interaction, enabled through at least one of the
+top-level connectors, at each execution round.
+
+Finally, \emph{priorities}\mdash defined by a strict partial order on
+the set of possible interactions\mdash narrow the choice among the
+enabled interactions at any given round.  The default priority is the
+so-called \emph{maximal progress}, whereby among any two interactions
+$a \subset b$ (as sets of ports), $b$ has higher priority than $a$.
+For example, the port $\NameOprnd.\PortFail$ will never fire alone in
+a global state, where both $\NameTimer.\PortStart$ and
+$\NameCtrl.\PortFail$ are enabled.
+%
+%% Adding priorities $\NameOprnd.\PortFinish < \NameCtrl.\PortReset$ and
+%% $\NameOprnd.\PortFinish < \NameOprnd.\PortResume$, ensures that, after
+%% a failure, the operation performed by $\NameOprnd$ cannot finish
+%% unless it is explicitly resumed or the system is reset.
+
+Application of the Failure Monitor architecture ensures that, whenever
+a failure is registered in the operand component, the system will be
+reset, unless a resumption is registered within $\mathrm{Max}$ time
+units (more details in Sect.~\ref{section:resultOA}).
 
@@
 \bibliographystyle{abbrv}
-\bibliography{biblio.bib}
+\bibliography{biblio}
 

### 2018-04-23 2018-Arch-pNets/arch-pNets.tex
Cleanup!!!

--- 2018-04-23 2018-Arch-pNets/arch-pNets.tex
@@
 We first define the set of actions a pLTS can use, let $a$
-range over action labels\removeSB{, $\symb{op}$ are operators, and $x_i$ range over
-variable names}. Action terms are\replaceSB{:}{{} of the form $\alpha=a((?x_i)^{i \in I}, 
+range over action labels. Action terms are  of the form $\alpha=a((?x_i)^{i \in I}, 
 \Expr_j^{j \in J})$, where $(?x_i)^{i \in I}$ are input variables, $\Expr_j^{j \in J})$ 
-are expressions.}\noteLH{Eric suggests to remove this: too precise. I 
-think last Expression should be removed not sure about the rest -- to be discussed}\noteSB{I agree: expressions are not needed, but it is nice to explain how action terms are formed }
-%\removeSBin{def of $\AlgA$, $p_i$, $\Expr$}
-%\[
-%\begin{array}[l]{rcl@{\quad}p{5.5cm}}
-%  \alpha\in\AlgA&::=&a(p_1,\ldots,p_n)&\text{action terms}\\
-%  p_i&::=& ?x~|~\Expr&\text{parameters (input variable or expression)}\\
-%  \Expr&::=& 
-%  \symb{Value}~|~x~|~\symb{op}(\Expr_1,..,\Expr_n)&\text{Expressions}
-%\end{array}
-%\]
-\removeSB{The input variables in an action term are those marked with a
-$\symb{?}$.}
-We additionally suppose that each input variable does not
-appear \replaceSB{somewhere else }{anywhere }in the same action term\replace[Maybe? Not sure this is necessary.\Simon]{:
-$p_i=?x\Rightarrow\forall j\neq i.\, x\notin \vars(p_j)$}{.}
+are expressions.
 
@@
 
-\todoLH{Guard syntax???}
 \begin{definition}[pNets]\label{def-pnets}
@@
 \item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
-  synchronisation vectors (\hl{$K\in\I_\P$}). $\forall k\!\in\! K,
-  \symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k\,|\,g_k$, where
+  synchronisation vectors. % (\hl{$K\in\I_\P$}). 
+$\forall k\!\in\! K,
+  \symb{SV}_k\!=\SV{\!\alpha_{l}^{l\in I_k \uplus J_k}}{\alpha'_k}{g_k}$, where
   $\alpha'_k\in \actions{\variables}$, $I_k\subseteq I$, $J_k\subseteq J$, and 
@@
 	holes involved in the transition\footnote{Formally, if $SV_k \!=\! \SV{\alpha_m^{m 
-	\in M}}{\alpha'}{e_b}$ is a synchronisation vector  of \pNet\  then $J=M\cap 
+	\in M}}{\alpha'}{g}$ is a synchronisation vector  of \pNet\  then $J=M\cap 
 	\Holes(\pNet)$, $I_2=M\cap \Leaves(\pNet)$,  $I_1=M\setminus J \setminus 
@@
     	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
-k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
+k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{g} 
 \\

### 2018-04-24 2018-Arch-pNets/arch-pNets.tex
1 comment
removed transitions in OT example
Open transitions are identified modulo logical equivalence on their predicate.

@@
   %
-  \todoSB{Do we actually need this?}
+  \todoSB{Do we actually need this?}\todoLH{I agree: I do not think we need this}
   \hl{The \emph{closed semantics} of $B$ is given by the LTS denoted
@@
 	a set of assignments that are the effects of the transition.
+Open transitions are identified modulo logical equivalence on their predicate.
 \end{definition}
@@
  $  OT_2  = \openrule{ 
-                       0 \xrightarrow{\delta}_{C_3} 1 ~~
-                            0 \xrightarrow{l}_{C_4} 0  ~~  
 							(P\mapsto \delta(x4), Q\mapsto accept(x4))               

### 2018-05-03 2016-Weak-FH-Bisim/WeakBisim.tex
Open transitions are identified modulo logical equivalence on their predicate.
mark ot eq done

@@
 \item[x] propager Tr2 dans l annexe
-\item add simple equivalence on OT
+\item[x] add simple equivalence on OT -- fait a minima 
 \item[x] explain the 2 level logic
@@
 	hold \emph{after the open transition}, they are represented as a substitution of the 
-	form $\{x_k\gets e_k\}^{k\in K}$ 
+	form $\subst{x_k\gets e_k}^{k\in K}$ 
 	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
-	variables of the open transition.
+	variables of the open transition. Open transitions are identified modulo logical equivalence on their predicate.
 \end{definition}

### 2018-05-03 2016-Weak-FH-Bisim/WeakBisim.tex
meeting with Rabea

--- 2018-04-23 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
-	variables of the open transition.
+	variables of the open transition. Open transitions are identified modulo logical equivalence on their predicate.
 \end{definition}
@@
     		{
-    		{\beta_j}^{j\in J^\prime}, \Pred, \uplus_{m\in I_1\uplus I_2} 
+    		{\beta_j}^{j\in J^\prime}, \Pred,  \biguplus_{m\in I_1\uplus I_2} 
     		\Post_m}
@@
 
-       	First,  $\forall y, \forall x, \forall p, J_1=J_{px}=J_{pxy}, 
-       	({s}',u_{pxy}|\Pred\,'_{{pxy}})\in \mathcal{R}''$. 
+       	First, we have $\forall y, \forall x, \forall p,  J_1=J_{px}=J_{pxy}, 
+       	({s}',u_{pxy}|\Pred\,'_{{pxy}})\in \mathcal{R}''$ for some $\Pred\,'_{{pxy}}$. 
        	Indeed for any 
@@
        	$y$, $t_{px}$
-       	relate ${s}'$ and $u_{pxy}$, indeed
+       	relates ${s}'$ and $u_{pxy}$, we have
        	$(s',t_{px}|\Pred_{{px}})\in \mathcal{R}$
@@
        		P'}$ is 
-       	the set of states relating ${s}'$ and $u_{pxy}$.
-       	Consequently, for all $p$, $x$, $y$, $\Pred_{px}\land 
+       	the set of states relating ${s}'$ and $u_{pxy}$ (the states used in the open transition must belong to the set of states ensuring the transitive relation).
+       	Additionally, for all $p$, $x$, $y$, $\Pred_{px}\land 
        	\Pred_{{pxy}}\implies 
        	\Pred\,'_{{pxy}}$ (this is one element of the  disjunction defining the 
-       	predicate 
+       	predicate $\Pred\,'_{{pxy}}$
        	relating ${s}'$ and $u_{pxy}$ in the definition of $\mathcal{R}''$).

### 2018-05-14 2018-Arch-pNets/arch-pNets.tex
few comments archi
a few more comments

@@
 \goesto{\PortStart, \TimerInit[]} \tstate{1}$, is a parameter of the
-architecture.
+architecture.\noteLH{It looks like Max is in zone, I do not understand}
 
@@
 
+\noteLHin{should we say that always epsilon C is the epsilon of C?}
+
 \begin{definition}[Architecture]
@@
   \]
-  defined by
+  defined by\noteLH{looks like this also depends on Pa}
 %
@@
 %
+\todoLH{Check when equivalence is defined}
   Suppose we have two architectures $A \arequiv A'$.  This does not

### 2018-05-15 2016-Weak-FH-Bisim/WeakBisim.tex

@@
 \begin{itemize}
-\item uniformiser p et P pour les pnets
+\item uniformiser p et P pour les pnets \RAB{Done for definitions 6 and 7. We will chek for lemmas 1 and 2}
 \item relectures
@@
 
-  For any pNet p, let $\Leaves(p) = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be 
+  For any pNet: \pNet, let $\Leaves(\pNet) = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be 
   the set of pLTS at its leaves,
-  then $States(p) = \{\triangleleft s_i^{i\in L}
+  then $States(\pNet) = \{\triangleleft s_i^{i\in L}
   \triangleright| \forall i\in L. s_i \in S_i\}$.
@@
 The initial state is defined as:
-$InitState(p) = \triangleleft {{s_i}_0}^{i\in L}  \triangleright$.
+$InitState(\pNet) = \triangleleft {{s_i}_0}^{i\in L}  \triangleright$.
 \end{definition}
@@
 the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
-\[\begin{array}{l}\Pred_{\symb{sv}}(\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
+\[\begin{array}{l}\Pred_{\symb{sv}} \Big(\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
 {\alpha'} 
-{e_b}, \alpha_i^{i\in I}, \beta_j^{j\in J}, \alpha)\Leftrightarrow \\~\qquad\qquad%\bigg(
+{e_b}, \alpha_i^{i\in I}, \beta_j^{j\in J}, \alpha\Big)\Leftrightarrow \\~\qquad\qquad%\bigg(
 %
@@
 	\label{def:operationalSemantics}
-	The semantics of a pNet $p$ is an open automaton $A = 
-	<Holes(p),States(p),InitState(p),
-	\mathcal{T}>$ where $\mathcal{T}$ is the smallest set of open transitions		satisfying the rules below:
+	The semantics of a pNet $\pNet$ is an open automaton $A\!= 
+	<\!\!Holes(\pNet),States(\pNet),InitState(\pNet),
+	\mathcal{T}\!\!>$ where $\mathcal{T}$ is the smallest set of open transitions		satisfying the rules below:
 %	\begin{itemize}
@@
 
-       	\begin{mathpar}
+       	\begin{mathpar} \qquad (*)
 
@@
 
-       	\begin{mathpar}
+       	\begin{mathpar} \qquad (**)
 
@@
        	\land \alpha_{px}\!=\!\alpha_{pxy} \land
-       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$\\.
+       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.\\
 

### 2018-05-15 2018-Arch-pNets/arch-pNets.tex

@@
     \noteSB{Added this}\hl{$\export : P \rightarrow 2^V$ 
-    the \emph{export function},}
+    the \emph{set of variables exported by each port},}
   \item $\goesto{}\, \subseteq
@@
     \in I} V_i$ and $\export : P \rightarrow 2^V$ such that, for any
-  $p \in P_i$, $\export(p) = \export[i](p)$.
+  $p \in P_i$, $\export(p) = \export[i](p)$. \noteLH{supp should go outside the definition}
 %
@@
 
+\noteLH{Ludo ou simon: essayer de remonter la description generique en debut de section}
 Connectors are hierarchical, tree-like structures with component ports

### 2018-05-16 2016-Weak-FH-Bisim/WeakBisim.tex
passe notations sur le papier weak

@@
 \def\Talg{\mathcal{T}_{\Sigma,\P}}
+\def\BoolExprs{\mathcal{B}_{\P}}
 Formally, we assume the existence of a term algebra $\Talg$,
@@
 data expressions $\mathcal{E}_\P$, including a set of boolean
-expressions $\mathcal{B}_{\P}$ ($\mathcal{B}_{\P}\subseteq\mathcal{E}_\P$).
+expressions $\BoolExprs$ ($\BoolExprs\subseteq\mathcal{E}_\P$).
 On top of $\mathcal{E}_\P$ we build the action algebra
@@
 range over action labels, $\symb{op}$ are operators, and $x_i$ range over
-variable names. Action terms are:
+variable names. Action terms of \pLTS s are:
 \[
@@
 		$\vars(e_b)\!\subseteq\! \vars(s)\cup\vars(\alpha)$, and
-		$\forall j\!\in\! J .\,\vars(e_j)\!\subseteq\! \vars(s)\cup\vars(\alpha)\land 
-		x_j\!\in\!\vars(s')$. %,  and $s= s'\Rightarrow J=\emptyset$. 
+		$\forall j\!\in\! J .\,\left(\vars(e_j)\!\subseteq\! \vars(s)\cup\vars(\alpha)\land 
+		x_j\!\in\!\vars(s') \right)$. %,  and $s= s'\Rightarrow J=\emptyset$. 
 \end{itemize}
@@
 not need to distinguish  input 
-variables. Action terms for pNets are defined as follows:
+variables. Action terms used in synchronisation vectors of pNets are defined as follows:
 \[\begin{array}[l]{rcl@{\quad}l}
@@
   J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
-$\alpha'_k$. $e_k \in \AlgB$ is a guard associated to the vector 
+$\alpha'_k$. $e_k \in \AlgB$ is a guard associated to the vector such that
 $\vars(e_k)\subseteq \bigcup_{l\in I_k\uplus J_k}{\vars({\alpha_l})}$.
@@
 input variables and we remove the
-\emph{input marker} of variables.
+\emph{input marker} (?) of variables.
 \[
@@
     J}\rangle} s'\in \to \} \\
-\Sortop(\mylangle \overline{\pNet}\!, %\pNet_i^{i\in I}, \Sort_j^{j\in J}
-\overline{\pNet}\!,
+\Sortop(\mylangle \overline{\pNet}\!, %\pNet_i^{i\in I}, 
+\overline{\Sort},
 \overline{\symb{SV}}\myrangle)
-=\{\alpha' |\, \overline{\alpha}%\alpha_j^{j\in J_k}
-\to\alpha'\in\set{\symb{SV}}\}
+=\{\alpha' |\, \SV{\overline{\alpha}}{\alpha'}{e_b}\in\set{\symb{SV}}\}
 \end{array}
@@
 \item
-The set of holes $\Holes(\pNet_{i_1})$ of a pNet is the indexes of the holes of the pNet 
+The set of holes $\Holes(\pNet)$ of a pNet is the indexes of the holes of the pNet 
 itself plus the indexes of all the holes of its subnets.
@@
 \Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset\\
-\Holes(\mylangle \pNet_i^{i\in I}\!,\Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) 
+\Holes(\mylangle \pNet_i^{i\in I}\!,\overline{\Sort}, \overline{\symb{SV}}\myrangle) 
 =J\uplus{\displaystyle \bigcup_{i\in 
@@
 \[\begin{array}{l}
-\Leaves(\mylangle S,s_0, \to\myrangle) \!=\!\{\mylangle S,s_0, \to\myrangle\}\\
+\Leaves(\mylangle S,s_0, \to\myrangle) \!=\!\emptyset\\%\{\mylangle S,s_0, \to\myrangle\}\\
 \Leaves(\mylangle \pNet_i^{i\in I}\!,%Sort_j^{j\in J}
@@
 	over the different variables of the
-	terms, labels, and states $s_i$, $\beta_j$, $s$, $\alpha$. \Post\ is a set of 
+	terms, labels, and states $\beta_j$, $s$, $\alpha$. \Post\ is a set of 
 	equations 
@@
 	form $\subst{x_k\gets e_k}^{k\in K}$ 
-	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
+	where $x_k$ are variables of $s'$, and $e_k$ are expressions over the other 
 	variables of the open transition. Open transitions are identified modulo logical equivalence on their predicate.
@@
 inference rule. They correspond to two different logical levels.
- The open transition is itself a logical implication, but using a simple logic (with the 
- expressive power that is given to the predicate and necessary include logical 
- propositions and equality). We differentiate classical (black) inference rules that use 
+ The open transition is itself a logical implication, but using a simple logic (this logic includes the boolean expressions $\BoolExprs$, boolean operators, and term equality).
+We differentiate classical (black) inference rules that use
  an expressive logic and are paper rules from open transition rules that use a simpler 
@@
 		$t\in \mathcal{T}$ there exist  $J'$ with  $J'
-		\subseteq J$, such that $t$ is an open transition over  $J'$,
+		\subseteq J$, such that $t$ is an open transition over  $J'$
 		and  $\mathcal{S}$.
@@
 
-We define states of open pNets as tuples of states, where we denote tuples
-in structured states as $\triangleleft\ldots\triangleright$ for distinguishing tuple 
+We define states of open pNets as tuples of states. We denote them
+ as $\triangleleft\ldots\triangleright$ for distinguishing tuple 
 states from other tuples.
@@
 \paragraph{Predicates:}
-Let
-$\mylangle\overline{\pNet},\overline{\Sort},\overline{\symb{SV}}\myrangle$
-be a pNet. Consider a synchronisation vector $\symb{SV}\in \overline{\symb{SV}}$. We 
+%Let
+%$\mylangle\overline{\pNet},\overline{\Sort},\overline{\symb{SV}}\myrangle$
+%be a pNet. 
+Consider a synchronisation vector $\symb{SV}$. We 
 define a
-predicate $\Pred$ relating
+predicate $\Predsv$ relating
 the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
-\[\begin{array}{l}\Pred_{\symb{sv}} \Big(\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
+\[\begin{array}{l}\Predsv \Big(\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
 {\alpha'} 
@@
 Somehow, this predicate entails a verification of satisfiability in the sense that if the 
-predicate $\Pred_{\symb{sv}}$ is not satisfiable, then the transition associated with the 
+predicate $\Predsv$ is not satisfiable, then the transition associated with the 
 synchronisation will not occur in the considered state.
@@
 At the upper level, the $ABP$ pNet has 2 holes and and $Protocol$ has
-a subnet. One of its possible transition (synchronizing the hole $P$
-with the $Protocol$) is:
+a subnet. One of its possible open transition (synchronizing the hole $P$
+with the \emph{Protocol}) is:
 
@@
     The global states here have the same structure than
-    in $OT\_2$, as the holes have no states. The assignment
+    in $OT_2$, as the holes have no states. The assignment
     $Post$ uses a variable from the action of hole $P$ to set the
@@
 
-  The \texttt{Protocol} pNet of Fig. \ref{schema:ABP-composed} has 4 controllers and no holes. One of its possible open-transition (the sender sending $(m,b)$ to the medium) is:
+  The \emph{Protocol} pNet of Fig. \ref{schema:ABP-composed} has 4 controllers and no holes. One of its possible open-transition (the sender sending $(m,b)$ to the medium) is:
 
@@
 %set of Holes and the set of Leaves.
-The semantics    instantiates \emph{fresh} variables, additionally, for an action 
+The semantics    instantiates fresh variables using the predicate $\fresh(x)$, additionally, for an action 
 $\alpha$, $\fresh(\alpha)$ means all variables in $\alpha$ are fresh.
@@
 	\begin{description}
-		\item[{\bf Tr1:}]
+		\item[{\TrUn:}]
 		$\inferrule
@@
 	sets, $I_2$ for subnets that are pLTSs, and $I_1$ for the others, $J$ is the set of 
-	holes involved in the transition\footnote{Formally, if $SV_k \!=\! \SV{\alpha_m^{m 
+	holes involved in the transition\footnote{Formally, if $SV_k \!=\! \SV{({\alpha'})_m^{m 
 	\in M}}{\alpha'}{e_b}$ is a synchronisation vector  of \pNet\  then $J=M\cap 
@@
 	\begin{description}
-		\item[{\bf Tr2:}]
+		\item[{\TrDeux:}]
 	\end{description}
@@
      J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
-    	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
-    	\Pred_{\symb{sv}}(SV_k,\alpha_m^{m\in (I_1\uplus I_2)},\beta_j^{j\in J},\alpha)\\ 
+    	\Pred = \bigwedge_{m\in I_1\uplus I_2}\!\! \Pred_m \land
+    	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2},\beta_j^{j\in J},\alpha)\\ 
     		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
@@
   open transition $OT_2$ of \texttt{EnableCompL} (see example page \pageref{OT:ABP-composed}).
-  The rule uses TR1 for the $\delta$ transition of $C_3$, for the $l$ transition of $C_4$, then combines the result using the $a_4$ vector of the bottom pNet node, and the $\underline{\delta(x)}$ vector of the top node.
-
-\begin{figure}[tb]
+  The rule uses \TrUn\ for the $\delta$ transition of $C_3$, for the $l$ transition of $C_4$, then combines the result using the $a_4$ vector of the bottom pNet node, and the $\underline{\delta(x)}$ vector of the top node.
+
+\begin{figure}[bh]
 \begin{mathpar}
@@
 each occurrence of a vector (= each time we instantiate rule
-Tr2). Similarly the state variables of each copy of a
+\TrDeux). Similarly the state variables of each copy of a
 given pLTS in the system, must be distinct, and those created for each
-application of Tr2 have to be fresh and all distinct. 
+application of \TrDeux\ have to be fresh and all distinct. 
 This will be implemented within the open-automaton generation algorithm,
@@
 build all possible deduction trees by application of the structural
-rules Tr1 and Tr2, using all applicable combinations
+rules \TrUn\ and \TrDeux, using all applicable combinations
 of synchronisation vectors.
@@
    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0, \mathcal{T}_2>$
-   are open automata where the set
-   of holes are equal 
-   and of the same sort.
+   are open automata with identical holes of the same sort.
 
@@
 substitutions $\Post_{OT}$ and $\Post_{OT_x}$ (parallelism is crucial
-inside each $\Post$ set but $\Post_{OT}$ is independent from
-$\Post_{OT_x}$), applying the assignments of the involved rules.
+inside each $\Post$ set but not between  $\Post_{OT}$ and
+$\Post_{OT_x}$ that are independent), applying the assignments of the involved rules.
 
@@
 => Open transitions are computed as a direct implementation of the algorithm above.
-Steps 2a-2b are merged: at each pNet node, after application of rule Tr2, the resulting OT is built from the premisses, without explicitely constructing the deduction tree.
+Steps 2a-2b are merged: at each pNet node, after application of rule \TrDeux, the resulting OT is built from the premisses, without explicitely constructing the deduction tree.
 \\
@@
        	\begin{mathpar}
-
        	\openrule
@@
        	{s \OTarrow {\alpha} {s}'}     	
-
        	\end{mathpar}
@@
 
-       	\begin{mathpar} \qquad (*)
-
+       	\begin{mathpar} 
        	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
@@
        		\beta_{j p x}^{j\in J_{px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
-       	{t_p \OTarrow {\alpha_{px}} t_{p x}}
+       	{t_p \OTarrow {\alpha_{px}} t_{p x}}\qquad (*)
        	%         \right)
@@
 
-       	\begin{mathpar} \qquad (**)
-
+       	\begin{mathpar}  	
        	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
@@
        		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
-       	{u \OTarrow {\alpha_{pxy}} u_{pxy}}
+       	{u \OTarrow {\alpha_{pxy}} u_{pxy}}\qquad (**)
        	%         \right)    	
-
        	\end{mathpar}
@@
        	\end{small}
-\TODO{From we will add notation (1) and (2)}   \LUDO{I do not remember what this TOD 
-means, Rabea?}      	
-       	We have, for all $p$
+From (*) and (**) we have, for all $p$
        	\begin{small}
@@
    \begin{small}\begin{proof}
-Consider rule TR2 in 
+Consider rule \TrDeux\ in 
        Definition~\ref{def:operationalSemantics}.
 
-\noindent\textbf{Tr2:}\\
+\noindent\TrDeux:\\
 	\noindent
@@
     	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
-    	\Pred_{\symb{sv}}(SV_k,\alpha_m^{m\in (I_1\uplus I_2)},\beta_j^{j\in J},\alpha)\\ 
+    	\Predsv(SV_k,\alpha_m^{m\in (I_1\uplus I_2)},\beta_j^{j\in J},\alpha)\\ 
     		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
@@
 \{j_0\}$;  the predicate is 
-$\Pred\,'=\bigwedge_{m\in I_k}\Pred_m  \land \Pred_{\symb{sv}}(SV_k,\alpha_m^{m\in 
+$\Pred\,'=\bigwedge_{m\in I_k}\Pred_m  \land \Predsv(SV_k,\alpha_m^{m\in 
 I},\beta_j^{j\in J\cup \{j_0\}},\alpha)$
-where\footnotemark[\thefootnote] $\Pred_{\symb{sv}}(SV_k,\alpha_m^{m\in I},\beta_j^{j\in 
+where\footnotemark[\thefootnote] $\Predsv(SV_k,\alpha_m^{m\in I},\beta_j^{j\in 
 J\cup 
@@
 
-       Consider each premise of the open transition (constructed by \textbf{Tr2} in 
+       Consider each premise of the open transition (constructed by \TrDeux\ in 
 Definition~\ref{def:operationalSemantics}). 
@@
 by hypothesis, the other open transitions are immediate consequence of the open 
-transition that can be performed by $P$ (premises of \textbf{Tr2}).
+transition that can be performed by $P$ (premises of \TrDeux).
 The set of moving leaves is the union of the moving leaves in the open transition for $P$ 
@@
 	\alpha=\alpha'\land \alpha_Q=\beta_{j_0}\land \beta_{j_0}=\alpha_{j_0}\land e_b$
- and by definition of $\Pred$ (as obtained by \textbf{Tr2}),
+ and by definition of $\Pred$ (as obtained by \TrDeux),
 	$\Pred\,''\iff \Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0}$. The post-condition 
@@
 To build a proof tree, we have to choose one synchronisation vector at
-each instantiation of rule Tr2, and one pLTS transition at each
-instantiation of rule Tr1. Each stage in the proof tree builds one
+each instantiation of rule \TrDeux, and one pLTS transition at each
+instantiation of rule \TrUn. Each stage in the proof tree builds one
 open-transition of the corresponding pNet node.  Let us explain in
@@
 where the first synch vector (for sub-group SG2) has length 2, and the
-second one (for the root pNet) has length 5. Using once the rule Tr1,
-and twice rule Tr2, we build a proof tree, in which the premisses
+second one (for the root pNet) has length 5. Using once the rule \TrUn,
+and twice rule \TrDeux, we build a proof tree, in which the premisses
 define the behaviour of a gateway pLTS (here
@@
 construct the proof tree, reduced here to applications of rule
-Tr1 for transitions of the pLTSs gw1 and gw2, and a single application of rule
-Tr2 for the synch vector HB at index 2:
+\TrUn for transitions of the pLTSs gw1 and gw2, and a single application of rule
+\TrDeux for the synch vector HB at index 2:
 
@@
 HB\_2, while keeping the state variables of $gw_1$ and $gw_2$, the
-intermediate $v$ created by Tr2, and the action variable of hole 
+intermediate $v$ created by \TrDeux, and the action variable of hole 
 $P3$. This yields finally predicate $Pred2$ :
@@
     {(s,\phi) \xrightarrow{\alpha\phi'} (s',\phi'') \in\llbracket\mylangle S,s_0,
-      \to\myrangle\rrbracket_\Phi}~~{\bf Tr1}
+      \to\myrangle\rrbracket_\Phi}~~{\TrUn}
 %         \end{mathpar}

### 2018-05-16 2016-Weak-FH-Bisim/WeakBisim.tex
Weak OT!

@@
 	hold \emph{after the open transition}, they are represented as a substitution of the 
-	form $\subst{x_k\gets e_k}^{k\in K}$ 
+	form $({x_k\gets e_k})^{k\in K}$ 
 	where $x_k$ are variables of $s'$, and $e_k$ are expressions over the other 
@@
 
+\TODO{Id(s) is the identity function on variables of state s}
+\begin{definition}[Non-observability of silent actions]
+An open automaton $A = <J,\mathcal{S},s_0,\mathcal{T}>$ \emph{cannot observe silent actions} if and only if for all $j$ in $J$ we have
+\[ \openrule
+         {
+           (j\mapsto\tau),\symb{True},\symb{Id}(s)}
+         {s \OTarrow {\tau} s}
+         \in \mathcal{T}
+\]
+\end{definition}
+
 Classically, we start by defining a derived transition relation based
@@
 
+We let $\gamma$ range over lists of action terms and use $\dotcup$ as the union that appends lists of action terms \TODO{write this properly}. $[a]$ is a list with a single element.
+
+We define $\vis{\overline\beta}$ as the mapping $\overline\beta$  without  invisible actions but where each element is now a list (if length 1).\\ $\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}$ s.t.
+$I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}$.
+
 \begin{definition}[Weak open transitions]
-  Let $A = <\overline{\LTS},J,\mathcal{S},s_0,\mathcal{T}>$ be an open automaton.
-  We define $\mathcal{T^*}$ the \emph{weak open transition relation}
-  with respect to a set of invisible actions $\InvAct$ as:
-
+  Let $A = <J,\mathcal{S},s_0,\mathcal{T}>$ be an open automaton. We derive the  weak invisible transition $\OTWeakarrow {\tau}$ from $\mathcal{T}$ as follows:
 \begin{mathpar}
@@
          {
-           \beta_j^{j\in J_1},\Pred,\Post}
+           \emptyset,\symb{True},Id(s)}
+         {s \OTWeakarrow {\tau} s}
+ \end{mathpar}
+and
+\begin{mathpar}
+\inferrule{
+ \openrule
+         {
+           \overline{\beta},\Pred,\Post}
+         {s \OTarrow {\tau} s'}
+\\
+ \openrule
+         {
+           \overline{\gamma},\Pred',({x_k\gets e_k})^{k\in K}   }
+         {s' \OTWeakarrow {\tau} s''}
+}
+{ \openrule
+         {
+           \vis{\overline{\beta}}\dotcup\overline{\gamma},\Pred\land\Pred'\subst{\Post},
+				({x_k\gets (e_k\subst \Post)})^{k\in K} } 
+         {s \OTWeakarrow {\tau} s''}
+}
+ \end{mathpar}
+
+And the general weak open transition $\OTWeakarrow {\alpha}$ as follows:
+\begin{mathpar}
+\inferrule{\openrule
+         {
+           \overline{\gamma_1},\Pred_1,\Post_1   }
+         {s \OTWeakarrow {\tau} s_1} 
+\\
+\openrule
+         {
+           \overline{\beta},\Pred_2,\Post_2  }
+         {s_1 \OTarrow {\alpha} s_2} 
+\\
+\openrule
+         {
+           \overline{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
+         {s_2 \OTWeakarrow {\tau} s'} 
+\\
+\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
+}
+{
+\openrule
+         {
+           \overline{\gamma_1}\dotcup \vis{\overline{\beta}}\dotcup\overline{\gamma_3},
+		\Pred,
+				({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K} } 
          {s \OTWeakarrow {\alpha} s'}
-         \in \mathcal{T}^*
+}
 \end{mathpar}
 
- iff there exists a sequence of open transitions
-         $OT_x^{x\in X} \subseteq \mathcal{T}$ such that:
-
- \TODO{Pas si simple !!!!!!!!!!!!!!!!!!!}
-
 \end{definition}
+
+\subsection{Non-observability and open pNets}
+\begin{definition}[Non-observability of silent actions]~\\
+A pNet $\mylangle \pNet_i^{i\in I} , \Sort_j^{j\in J}, \overline{\symb{SV}}\myrangle$
+ \emph{cannot observe silent actions} if it verifies:\\ $\forall i\in I\uplus J.\, \SV{(i\mapsto \tau)}{\tau}{\symb{True}}\in \overline{\symb{SV}}$ and $\forall i,j\in I\uplus J.\,i\neq j \Rightarrow \alpha_i\neq\tau$
+\end{definition}
+
+\begin{property}[pNets that cannot observe silent actions]
+The open semantics of a pNets that cannot observe silent actions is an open automaton that  cannot observe silent actions.
+\end{property}
 

### 2018-05-17 2016-Weak-FH-Bisim/WeakBisim.tex
more on weak ot and weak automata

@@
 %notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
-\begin{definition}[Open transitions]
+\begin{definition}[Open transitions]\label{def:OT}
 	\label{def:OpenTransitions}
@@
 \begin{mathpar}
-    \mprset {vskip=1ex}
+    \mprset {vskip=.8ex}
 \inferrule
@@
 $I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}$.
-
-\begin{definition}[Weak open transitions]
-  Let $A = <J,\mathcal{S},s_0,\mathcal{T}>$ be an open automaton. We derive the  weak invisible transition $\OTWeakarrow {\tau}$ from $\mathcal{T}$ as follows:
+\def\WT{\mathcal{WT}}
+\begin{definition}[Weak open transition]\label{def:weakOT}
+A weak open transition over a
+	set $J$ of holes with sorts $\Sort_j^{j\in J}$ and a set of states $\mathcal{S}$ is 
+	a structure of the form:	
 \begin{mathpar}
@@
          {
+           \gamma_j^{j\in J},\symb{True},Id(s)}
+         {s \OTWeakarrow {\alpha} s}
+ \end{mathpar}
+	Where $s, s'\in\mathcal{S}$ and $\gamma_j$
+        is a list of transitions of the hole $j$, with each element of the list in $\Sort_j$. $\alpha$ is an action 
+        label denoting the resulting action
+        of this open transition. \Pred\ and \Post\ are defined similarly to Definition~\ref{def:OT}. We use $\WT$ to range over sets of weak open transitions.
+
+A weak open automaton $<J,\mathcal{S},s_0,\WT>$ is similar to an open automaton  except that $\WT$ is a set of weak open transitions over $J$ and $\mathcal{S}$.
+\end{definition}
+
+\begin{definition}[Building a weak open automaton]\label{def:buildweakOT}
+  Let $A = <J,\mathcal{S},s_0,\mathcal{T}>$ be an open automaton. 
+The weak open automaton \emph{derived} from $A$ is an open automaton  $<J,\mathcal{S},s_0,\WT>$ where $\WT$ is derived from $\mathcal{T}$ as follows
+
+\noindent{\bf Invisible $\tau$ transitions:}
+\begin{mathpar}
+ \openrule
+         {
            \emptyset,\symb{True},Id(s)}
-         {s \OTWeakarrow {\tau} s}
+         {s \OTWeakarrow {\tau} s} \in \WT
  \end{mathpar}
@@
 \begin{mathpar}
+  \mprset {vskip=.5ex}
 \inferrule{
@@
            \overline{\beta},\Pred,\Post}
-         {s \OTarrow {\tau} s'}
+         {s \OTarrow {\tau} s'} \in \mathcal{T}
 \\
@@
            \overline{\gamma},\Pred',({x_k\gets e_k})^{k\in K}   }
-         {s' \OTWeakarrow {\tau} s''}
+         {s' \OTWeakarrow {\tau} s''} \in \WT
 }
@@
 				({x_k\gets (e_k\subst \Post)})^{k\in K} } 
-         {s \OTWeakarrow {\tau} s''}
+         {s \OTWeakarrow {\tau} s''} \in \WT
 }
@@
 
-And the general weak open transition $\OTWeakarrow {\alpha}$ as follows:
+\noindent{\bf Other transitions:}
 \begin{mathpar}
-\inferrule{\openrule
+  \mprset {vskip=.5ex}
+\inferrule {\openrule
          {
            \overline{\gamma_1},\Pred_1,\Post_1   }
-         {s \OTWeakarrow {\tau} s_1} 
+         {s \OTWeakarrow {\tau} s_1} \in \WT
+\qquad\qquad
+\openrule
+         {
+           \overline{\beta},\Pred_2,\Post_2  }
+         {s_1 \OTarrow {\alpha} s_2} \in \mathcal{T}
 \\
@@
          {
-           \overline{\beta},\Pred_2,\Post_2  }
-         {s_1 \OTarrow {\alpha} s_2} 
-\\
-\openrule
-         {
            \overline{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
-         {s_2 \OTWeakarrow {\tau} s'} 
+         {s_2 \OTWeakarrow {\tau} s'} \in\WT
 \\
@@
 				({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K} } 
-         {s \OTWeakarrow {\alpha} s'}
+         {s \OTWeakarrow {\alpha} s'} \in\WT
 }
@@
 \noindent
-Let $A_1$ and $A_2$ be open automata, and $\mathcal{R}$ a relation over
-$\mathcal{S}_1$ and $\mathcal{S}_2$, as in Definition \ref{def-FH-bisim}.
+Let $A_1 = <J,\mathcal{S}_1, s_0,
+    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata.
+Let $<J,\mathcal{S}_1, s_0,
+    \WT_1>$ and $<J,\mathcal{S}_2,t_0,  \WT_2>$ be the
+weak open automata derived from $A_1$ and $A_2$ respectively.
+Let $\mathcal{R}$ a relation over
+$\mathcal{S}_1$ and $\mathcal{S}_2$, as in Definition~\ref{def-FH-bisim}.
 
@@
    $\mathcal{R}$ is a weak FH-bisimulation iff for any  states
-$s\in\mathcal{S}_1$ and\\
-$t\in\mathcal{S}_2$, $(s,t|\Pred)\in\mathcal{R}$, we 
+$s\in\mathcal{S}_1$ and
+$t\in\mathcal{S}_2$ such that $(s,t|\Pred)\in\mathcal{R}$, we 
    have the following:
@@
 \end{mathpar}
- there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2^*$:
+ there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
  \begin{mathpar}
@@
          {
-           \beta_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
          {t \OTWeakarrow {\alpha_x} t_x}

### 2018-05-17 2016-Weak-FH-Bisim/WeakBisim.tex
typs

--- 2018-05-16 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 \begin{itemize}
-\item uniformiser p et P pour les pnets \RAB{Done for definitions 6 and 7. We will chek for lemmas 1 and 2}
+\item uniformiser p et P pour les pnets \RAB{Done for definitions 6 and 7. We will check for lemmas 1 and 2}
 \item relectures
@@
 \def\Talg{\mathcal{T}_{\Sigma,\P}}
-\def\BoolExprs{\mathcal{B}_{\P}}
 Formally, we assume the existence of a term algebra $\Talg$,
@@
 data expressions $\mathcal{E}_\P$, including a set of boolean
-expressions $\BoolExprs$ ($\BoolExprs\subseteq\mathcal{E}_\P$).
+expressions $\mathcal{B}_{\P}$ ($\mathcal{B}_{\P}\subseteq\mathcal{E}_\P$).
 On top of $\mathcal{E}_\P$ we build the action algebra
@@
 range over action labels, $\symb{op}$ are operators, and $x_i$ range over
-variable names. Action terms of \pLTS s are:
+variable names. Action terms are:
 \[
@@
 		$\vars(e_b)\!\subseteq\! \vars(s)\cup\vars(\alpha)$, and
-		$\forall j\!\in\! J .\,\left(\vars(e_j)\!\subseteq\! \vars(s)\cup\vars(\alpha)\land 
-		x_j\!\in\!\vars(s') \right)$. %,  and $s= s'\Rightarrow J=\emptyset$. 
+		$\forall j\!\in\! J .\,\vars(e_j)\!\subseteq\! \vars(s)\cup\vars(\alpha)\land 
+		x_j\!\in\!\vars(s')$. %,  and $s= s'\Rightarrow J=\emptyset$. 
 \end{itemize}
@@
 not need to distinguish  input 
-variables. Action terms used in synchronisation vectors of pNets are defined as follows:
+variables. Action terms for pNets are defined as follows:
 \[\begin{array}[l]{rcl@{\quad}l}
@@
   J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
-$\alpha'_k$. $e_k \in \AlgB$ is a guard associated to the vector such that
+$\alpha'_k$. $e_k \in \AlgB$ is a guard associated to the vector 
 $\vars(e_k)\subseteq \bigcup_{l\in I_k\uplus J_k}{\vars({\alpha_l})}$.
@@
 input variables and we remove the
-\emph{input marker} (?) of variables.
+\emph{input marker} of variables.
 \[
@@
     J}\rangle} s'\in \to \} \\
-\Sortop(\mylangle \overline{\pNet}\!, %\pNet_i^{i\in I}, 
-\overline{\Sort},
+\Sortop(\mylangle \overline{\pNet}\!, %\pNet_i^{i\in I}, \Sort_j^{j\in J}
+\overline{\pNet}\!,
 \overline{\symb{SV}}\myrangle)
-=\{\alpha' |\, \SV{\overline{\alpha}}{\alpha'}{e_b}\in\set{\symb{SV}}\}
+=\{\alpha' |\, \overline{\alpha}%\alpha_j^{j\in J_k}
+\to\alpha'\in\set{\symb{SV}}\}
 \end{array}
@@
 \item
-The set of holes $\Holes(\pNet)$ of a pNet is the indexes of the holes of the pNet 
+The set of holes $\Holes(\pNet_{i_1})$ of a pNet is the indexes of the holes of the pNet 
 itself plus the indexes of all the holes of its subnets.
@@
 \Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset\\
-\Holes(\mylangle \pNet_i^{i\in I}\!,\overline{\Sort}, \overline{\symb{SV}}\myrangle) 
+\Holes(\mylangle \pNet_i^{i\in I}\!,\Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) 
 =J\uplus{\displaystyle \bigcup_{i\in 
@@
 \[\begin{array}{l}
-\Leaves(\mylangle S,s_0, \to\myrangle) \!=\!\emptyset\\%\{\mylangle S,s_0, \to\myrangle\}\\
+\Leaves(\mylangle S,s_0, \to\myrangle) \!=\!\{\mylangle S,s_0, \to\myrangle\}\\
 \Leaves(\mylangle \pNet_i^{i\in I}\!,%Sort_j^{j\in J}
@@
 	over the different variables of the
-	terms, labels, and states $\beta_j$, $s$, $\alpha$. \Post\ is a set of 
+	terms, labels, and states $s_i$, $\beta_j$, $s$, $\alpha$. \Post\ is a set of 
 	equations 
@@
 	form $\subst{x_k\gets e_k}^{k\in K}$ 
-	where $x_k$ are variables of $s'$, and $e_k$ are expressions over the other 
+	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
 	variables of the open transition. Open transitions are identified modulo logical equivalence on their predicate.
@@
 inference rule. They correspond to two different logical levels.
- The open transition is itself a logical implication, but using a simple logic (this logic includes the boolean expressions $\BoolExprs$, boolean operators, and term equality).
-We differentiate classical (black) inference rules that use
+ The open transition is itself a logical implication, but using a simple logic (with the 
+ expressive power that is given to the predicate and necessary include logical 
+ propositions and equality). We differentiate classical (black) inference rules that use 
  an expressive logic and are paper rules from open transition rules that use a simpler 
@@
 		$t\in \mathcal{T}$ there exist  $J'$ with  $J'
-		\subseteq J$, such that $t$ is an open transition over  $J'$
+		\subseteq J$, such that $t$ is an open transition over  $J'$,
 		and  $\mathcal{S}$.
@@
 
-We define states of open pNets as tuples of states. We denote them
- as $\triangleleft\ldots\triangleright$ for distinguishing tuple 
+We define states of open pNets as tuples of states, where we denote tuples
+in structured states as $\triangleleft\ldots\triangleright$ for distinguishing tuple 
 states from other tuples.
@@
 \paragraph{Predicates:}
-%Let
-%$\mylangle\overline{\pNet},\overline{\Sort},\overline{\symb{SV}}\myrangle$
-%be a pNet. 
-Consider a synchronisation vector $\symb{SV}$. We 
+Let
+$\mylangle\overline{\pNet},\overline{\Sort},\overline{\symb{SV}}\myrangle$
+be a pNet. Consider a synchronisation vector $\symb{SV}\in \overline{\symb{SV}}$. We 
 define a
-predicate $\Predsv$ relating
+predicate $\Pred$ relating
 the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
-\[\begin{array}{l}\Predsv \Big(\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
+\[\begin{array}{l}\Pred_{\symb{sv}} \Big(\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
 {\alpha'} 
@@
 Somehow, this predicate entails a verification of satisfiability in the sense that if the 
-predicate $\Predsv$ is not satisfiable, then the transition associated with the 
+predicate $\Pred_{\symb{sv}}$ is not satisfiable, then the transition associated with the 
 synchronisation will not occur in the considered state.
@@
 At the upper level, the $ABP$ pNet has 2 holes and and $Protocol$ has
-a subnet. One of its possible open transition (synchronizing the hole $P$
-with the \emph{Protocol}) is:
+a subnet. One of its possible transition (synchronizing the hole $P$
+with the $Protocol$) is:
 
@@
     The global states here have the same structure than
-    in $OT_2$, as the holes have no states. The assignment
+    in $OT\_2$, as the holes have no states. The assignment
     $Post$ uses a variable from the action of hole $P$ to set the
@@
 
-  The \emph{Protocol} pNet of Fig. \ref{schema:ABP-composed} has 4 controllers and no holes. One of its possible open-transition (the sender sending $(m,b)$ to the medium) is:
+  The \texttt{Protocol} pNet of Fig. \ref{schema:ABP-composed} has 4 controllers and no holes. One of its possible open-transition (the sender sending $(m,b)$ to the medium) is:
 
@@
 %set of Holes and the set of Leaves.
-The semantics    instantiates fresh variables using the predicate $\fresh(x)$, additionally, for an action 
+The semantics    instantiates \emph{fresh} variables, additionally, for an action 
 $\alpha$, $\fresh(\alpha)$ means all variables in $\alpha$ are fresh.
@@
 	\begin{description}
-		\item[{\TrUn:}]
+		\item[{\bf Tr1:}]
 		$\inferrule
@@
 	sets, $I_2$ for subnets that are pLTSs, and $I_1$ for the others, $J$ is the set of 
-	holes involved in the transition\footnote{Formally, if $SV_k \!=\! \SV{({\alpha'})_m^{m 
+	holes involved in the transition\footnote{Formally, if $SV_k \!=\! \SV{\alpha_m^{m 
 	\in M}}{\alpha'}{e_b}$ is a synchronisation vector  of \pNet\  then $J=M\cap 
@@
 	\begin{description}
-		\item[{\TrDeux:}]
+		\item[{\bf Tr2:}]
 	\end{description}
@@
      J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
-    	\Pred = \bigwedge_{m\in I_1\uplus I_2}\!\! \Pred_m \land
-    	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2},\beta_j^{j\in J},\alpha)\\ 
+    	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
+    	\Pred_{\symb{sv}}(SV_k,\alpha_m^{m\in (I_1\uplus I_2)},\beta_j^{j\in J},\alpha)\\ 
     		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
@@
   open transition $OT_2$ of \texttt{EnableCompL} (see example page \pageref{OT:ABP-composed}).
-  The rule uses \TrUn\ for the $\delta$ transition of $C_3$, for the $l$ transition of $C_4$, then combines the result using the $a_4$ vector of the bottom pNet node, and the $\underline{\delta(x)}$ vector of the top node.
-
-\begin{figure}[bh]
+  The rule uses TR1 for the $\delta$ transition of $C_3$, for the $l$ transition of $C_4$, then combines the result using the $a_4$ vector of the bottom pNet node, and the $\underline{\delta(x)}$ vector of the top node.
+
+\begin{figure}[tb]
 \begin{mathpar}
@@
 each occurrence of a vector (= each time we instantiate rule
-\TrDeux). Similarly the state variables of each copy of a
+Tr2). Similarly the state variables of each copy of a
 given pLTS in the system, must be distinct, and those created for each
-application of \TrDeux\ have to be fresh and all distinct. 
+application of Tr2 have to be fresh and all distinct. 
 This will be implemented within the open-automaton generation algorithm,
@@
 build all possible deduction trees by application of the structural
-rules \TrUn\ and \TrDeux, using all applicable combinations
+rules Tr1 and Tr2, using all applicable combinations
 of synchronisation vectors.
@@
    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0, \mathcal{T}_2>$
-   are open automata with identical holes of the same sort.
+   are open automata where the set
+   of holes are equal 
+   and of the same sort.
 
@@
 substitutions $\Post_{OT}$ and $\Post_{OT_x}$ (parallelism is crucial
-inside each $\Post$ set but not between  $\Post_{OT}$ and
-$\Post_{OT_x}$ that are independent), applying the assignments of the involved rules.
+inside each $\Post$ set but $\Post_{OT}$ is independent from
+$\Post_{OT_x}$), applying the assignments of the involved rules.
 
@@
 => Open transitions are computed as a direct implementation of the algorithm above.
-Steps 2a-2b are merged: at each pNet node, after application of rule \TrDeux, the resulting OT is built from the premisses, without explicitely constructing the deduction tree.
+Steps 2a-2b are merged: at each pNet node, after application of rule Tr2, the resulting OT is built from the premisses, without explicitely constructing the deduction tree.
 \\
@@
        	\begin{mathpar}
+
        	\openrule
@@
        	{s \OTarrow {\alpha} {s}'}
+
        	\end{mathpar}
@@
 
-       	\begin{mathpar} 
+       	\begin{mathpar} \qquad (*)
+
        	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
@@
        		\beta_{j p x}^{j\in J_{px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
-       	{t_p \OTarrow {\alpha_{px}} t_{p x}}\qquad (*)
+       	{t_p \OTarrow {\alpha_{px}} t_{p x}}
        	%         \right)
@@
 
-       	\begin{mathpar}  	
+       	\begin{mathpar} \qquad (**)
+
        	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
@@
        		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
-       	{u \OTarrow {\alpha_{pxy}} u_{pxy}}\qquad (**)
+       	{u \OTarrow {\alpha_{pxy}} u_{pxy}}
        	%         \right)
+
        	\end{mathpar}
@@
        	\end{small}
-From (*) and (**) we have, for all $p$
+\TODO{From we will add notation (1) and (2)}   \LUDO{I do not remember what this TOD 
+means, Rabea?}      	
+       	We have, for all $p$
        	\begin{small}
@@
    \begin{small}\begin{proof}
-Consider rule \TrDeux\ in 
+Consider rule TR2 in 
        Definition~\ref{def:operationalSemantics}.
 
-\noindent\TrDeux:\\
+\noindent\textbf{Tr2:}\\
 	\noindent
@@
     	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
-    	\Predsv(SV_k,\alpha_m^{m\in (I_1\uplus I_2)},\beta_j^{j\in J},\alpha)\\ 
+    	\Pred_{\symb{sv}}(SV_k,\alpha_m^{m\in (I_1\uplus I_2)},\beta_j^{j\in J},\alpha)\\ 
     		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
@@
 \{j_0\}$;  the predicate is 
-$\Pred\,'=\bigwedge_{m\in I_k}\Pred_m  \land \Predsv(SV_k,\alpha_m^{m\in 
+$\Pred\,'=\bigwedge_{m\in I_k}\Pred_m  \land \Pred_{\symb{sv}}(SV_k,\alpha_m^{m\in 
 I},\beta_j^{j\in J\cup \{j_0\}},\alpha)$
-where\footnotemark[\thefootnote] $\Predsv(SV_k,\alpha_m^{m\in I},\beta_j^{j\in 
+where\footnotemark[\thefootnote] $\Pred_{\symb{sv}}(SV_k,\alpha_m^{m\in I},\beta_j^{j\in 
 J\cup 
@@
 
-       Consider each premise of the open transition (constructed by \TrDeux\ in 
+       Consider each premise of the open transition (constructed by \textbf{Tr2} in 
 Definition~\ref{def:operationalSemantics}). 
@@
 by hypothesis, the other open transitions are immediate consequence of the open 
-transition that can be performed by $P$ (premises of \TrDeux).
+transition that can be performed by $P$ (premises of \textbf{Tr2}).
 The set of moving leaves is the union of the moving leaves in the open transition for $P$ 
@@
 	\alpha=\alpha'\land \alpha_Q=\beta_{j_0}\land \beta_{j_0}=\alpha_{j_0}\land e_b$
- and by definition of $\Pred$ (as obtained by \TrDeux),
+ and by definition of $\Pred$ (as obtained by \textbf{Tr2}),
 	$\Pred\,''\iff \Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0}$. The post-condition 
@@
 To build a proof tree, we have to choose one synchronisation vector at
-each instantiation of rule \TrDeux, and one pLTS transition at each
-instantiation of rule \TrUn. Each stage in the proof tree builds one
+each instantiation of rule Tr2, and one pLTS transition at each
+instantiation of rule Tr1. Each stage in the proof tree builds one
 open-transition of the corresponding pNet node.  Let us explain in
@@
 where the first synch vector (for sub-group SG2) has length 2, and the
-second one (for the root pNet) has length 5. Using once the rule \TrUn,
-and twice rule \TrDeux, we build a proof tree, in which the premisses
+second one (for the root pNet) has length 5. Using once the rule Tr1,
+and twice rule Tr2, we build a proof tree, in which the premisses
 define the behaviour of a gateway pLTS (here
@@
 construct the proof tree, reduced here to applications of rule
-\TrUn for transitions of the pLTSs gw1 and gw2, and a single application of rule
-\TrDeux for the synch vector HB at index 2:
+Tr1 for transitions of the pLTSs gw1 and gw2, and a single application of rule
+Tr2 for the synch vector HB at index 2:
 
@@
 HB\_2, while keeping the state variables of $gw_1$ and $gw_2$, the
-intermediate $v$ created by \TrDeux, and the action variable of hole 
+intermediate $v$ created by Tr2, and the action variable of hole 
 $P3$. This yields finally predicate $Pred2$ :
@@
     {(s,\phi) \xrightarrow{\alpha\phi'} (s',\phi'') \in\llbracket\mylangle S,s_0,
-      \to\myrangle\rrbracket_\Phi}~~{\TrUn}
+      \to\myrangle\rrbracket_\Phi}~~{\bf Tr1}
 %         \end{mathpar}

### 2018-05-22 2016-Weak-FH-Bisim/WeakBisim.tex
reunion avec rabea

--- 2018-05-17 2016-Weak-FH-Bisim/WeakBisim.tex
@@
            \gamma_j^{j\in J},\symb{True},Id(s)}
-         {s \OTWeakarrow {\alpha} s}
+         {s \OTWeakarrow {\alpha} s'}
  \end{mathpar}
@@
 \hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-   \left( \forall j. \beta_j=\beta_{jx}  \Rightarrow \Pred_{OT_x}
+   \left( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
      \land \alpha\!=\!\alpha_x \land  
@@
  \item  and symmetrically any open transition from $t$ in $\mathcal{T}_2$ can be 
-      covered by a set of weak transitions from $s$ in $\mathcal{T}_1^*$.
+      covered by a set of weak transitions from $s$ in $\WT_1$.
  \end{itemize}
 
-Two pNets are Weak FH-bisimilar if there exist a relation between their associated open
-automata that is an Weak FH-bisimulation and their initial states are equivalent.
-\TODO{LUDO: define equivalent}
+Two pNets are Weak FH-bisimilar if there exist a relation between their associated 
+automata that is a Weak FH-bisimulation and their initial states are in the relation, i.e. 
+the predicate associated to the relation between the initial states is true.
  \end{definition}

### 2018-05-23 2016-Weak-FH-Bisim/WeakBisim.tex
adding thm weak bisim + corol comp

@@
   between INRIA and ECNU, Shanghai}}
-\author{ Ludovic Henrio\inst{1}  \ \ \  Eric Madelaine\inst{1,2} \ \ \ Rabéa}
+\author{ Ludovic Henrio\inst{1}  \ \ \  Eric Madelaine\inst{1,2} \ \ \ Rab\'ea}
 \institute{Univ. of Nice Sophia Antipolis, CNRS, UMR 7271, 06900 Sophia Antipolis, France
@@
 \begin{itemize}
-\item uniformiser p et P pour les pnets \RAB{Done for definitions 6 and 7. We will chek for lemmas 1 and 2}
-\item relectures
+\item [x] uniformiser p et P pour les pnets 
+\item [x] relectures
 \end{itemize}
@@
 \begin{minipage}{0.69\linewidth} 	Suppose that
-   $A_1 = <J,\mathcal{S}_1, s_0,
-   \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0, \mathcal{T}_2>$
+   $A_1 = <\!J,\mathcal{S}_1, s_0,
+   \mathcal{T}_1\!>$ and $A_2 = <\!J,\mathcal{S}_2,t_0, \mathcal{T}_2\!>$
    are open automata with identical holes of the same sort.
@@
          {
-           \overline{\gamma},\Pred',({x_k\gets e_k})^{k\in K}   }
+           \overline{\gamma},\Pred\,',({x_k\gets e_k})^{k\in K}   }
          {s' \OTWeakarrow {\tau} s''} \in \WT
@@
          {
-           \vis{\overline{\beta}}\dotcup\overline{\gamma},\Pred\land\Pred'\subst{\Post},
-				({x_k\gets (e_k\subst \Post)})^{k\in K} } 
+           \vis{\overline{\beta}}\dotcup\overline{\gamma},\Pred\land\Pred\,'\subst{\Post\,},
+				({x_k\gets (e_k\subst{\Post\,})})^{k\in K} } 
          {s \OTWeakarrow {\tau} s''} \in \WT
@@
 \end{definition}
+
+\begin{theorem}[Weak FH-Bisimulation is an equivalence]\label{thm-weak-equiv} Suppose $\mathcal{R}$ 
+is a weak FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
+reflexive, symmetric and transitive.
+\end{theorem}
+
+\TODO{We will discuss this corollary and the title.}
+
+\begin{corollary}[Weak Composability]
+	Consider two weak FH-bisimilar pNets with an arbitrary number of holes, when replacing, 
+	inside those two original pNets, a subset of the holes by FH-bisimilar pNets, we 
+	obtain two weak FH-bisimilar pNets.
+\end{corollary}
 

### 2018-05-23 2016-Weak-FH-Bisim/WeakBisim.tex
Definition 7

@@
 	\label{def:operationalSemantics}
-	The semantics of a pNet $\pNet$ is an open automaton $A\!= 
-	<\!\!Holes(\pNet),States(\pNet),InitState(\pNet),
-	\mathcal{T}\!\!>$ where $\mathcal{T}$ is the smallest set of open transitions		satisfying the rules below:
+	The semantics of a pNet, $\pNet$ is an open automaton $A\!= 
+	<\!\!Holes(\pNet),States(\pNet),InitState(\pNet),\mathcal{T}\!\!>$ where $\mathcal{T}$   is the smallest set of open transitions such that $\mathcal{T}=\{OT\,|\,\pNet \models OT \}$ and	$\pNet \models OT$	is defined by the following  rules:
 %	\begin{itemize}

### 2018-05-24 2017-Xudong-SMT/AVOCS-2018-pre-proceeding.tex
Add two version of AVOCS paper.
-pre-proceeding will be submited to AVOCS later.
-RR is the research report.

--- 2018-04-23 2017-Xudong-SMT/AVOCS-2018.tex
@@
 languages. They are endowed with a symbolic operational semantics in
-terms of so-called ``Open Automata''. This allows to check properties of
+terms of so-called ``Open Automata''. This allows us to check properties of
 such systems in a compositional manner. 
-We implement an algorithm computing this semantics,
+We implement an algorithm computing these semantics,
 building predicates expressing the synchronization conditions
@@
 systems, synchronous, asynchronous, or heterogeneous. They are used in
-VerCors, a platform for designing and 
+VerCors~\cite{HKLM:Foclasa14}, a platform for designing and 
 verifying distributed systems, as the intermediate language for various
@@
 other algebras or  program skeletons.
-The operational semantic of an (open) pNet is defined as an
+The operational semantics of an (open) pNet is defined as an
 Open Automaton in which Open Transitions contain logical predicates
@@
 global behaviour of the system. In the previous publication,
-only a sketch of a procedure allowing to compute this semantics was
+only a sketch of a procedure allowing to compute these semantics was
 presented, together with a proof of finiteness of the open automaton, under
@@
 
-Implementing this semantics raised several challenges, in order:
+Implementing these semantics raised several challenges, in order:
 \begin{itemize}
@@
 
-In the long goal, we want to be able to check the equivalence between
+In the long term, we want to be able to check the equivalence between
 open systems encoded as pNets. The equivalence between pNets is
@@
 \begin{itemize}
-\item We define the open automaton generation algorithm, and we
+\item We define the open automaton generation algorithm. We
   implemented a full working prototype, within the 
@@
   semantics rules from~\cite{henrio:Forte2016}, and add features in
-  the algorithm to deal the full 
+  the algorithm to deal with the full 
   model, including management of variables and assignments.
@@
 based on the satisfiability modulo 
-theories (SMT), is mainly applied in extended static checking, test case
+theories framework (SMT), is mainly applied in extended static checking, test case
 generation, and predicate abstraction.
@@
 In practice, the parameterization of the pNet model by some specific
-action algebra is realized by the definition of an many-sorted ``algebra
+action algebra is realized by the definition of a many-sorted ``algebra
 presentation''. It will be used to check the
@@
 $s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
-		J}\rangle} s'\in \to $ then 
+		J}\rangle} s'$ then 
                 $\vars(e_b)\!\subseteq\! \vars(s)\cup\vars(\alpha)$, and
@@
 		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred\,, \Post}
-	{s \xrightarrow {v}s'}\,,
+	{s \xrightarrow {\alpha}s'}\,,
 	\end{mathpar}
@@
 Note that in the previous sections, the OTs were displayed in a
-  simplied, human readable form. The input and output of our tool, and
+  simplified, human readable form. The input and output of our tool, and
   also the generated SMTlib fragments, are
@@
 predicate to be checked, encoded as a set of assertions.
-Here we display also the proof generated by Z3;
+Here we display also the diagnosis (``sat'' or ``unsat'') generated by Z3;
 %% \noteSB{I am not sure I understand the entire message of this phrase}\hl{though in practice our tool only needs the brute information ``sat''
 %% or ``unsat''.
-The result "unsat" in the output is just what we expected.
+%% The result "unsat" in the output is just what we expected.
+%% If the result is ``sat'', and more details are needed, Z3 can exhibit a
+%% model (i.e. an instanciation of the variables) showing the satisfiability.
 % as appears in the ``unsat'' proof generated by Z3 in which ``\{= ?x66 ?x70\}'' is shown to be false (see Fig. \ref{schema:smt-lib})
@@
 compositional and parametric approach. Still one may wonder if the price
-for analysing our our symbolic transitions will not make the approach
-inapplicable. Here we tried a
-slighly bigger example, assembling 2 Failure controlers. In
+for analysing our symbolic transitions will not make the approach too expensive
+in term of computing time. We tried a
+slighly bigger example, assembling 2 Failure controllers. In
 appendix~\ref{appendix:scalingup}, we show that Z3 can check the
@@
 Comparing this with the previous result on on a single subnet, we
-found that this was caused by a input mistake in a synchronisation vector.
+found that this was caused by an input mistake in a synchronisation vector.
 

### 2018-05-24 2018-Arch-pNets/arch-pNets.tex
re-new figure 2
passe notations sur le papier weak
Distributed the text from the running example section earlier in the text, after corresponding definitions

--- 2018-05-14 2018-Arch-pNets/arch-pNets.tex
@@
 \newcommand{\fig}[1]{Fig.~\ref{fig:#1}}
+\newcommand{\Fig}[1]{Figure~\ref{fig:#1}}
 \newcommand{\figs}[2]{Fig.~\ref{fig:#1} and~\ref{fig:#2}}
@@
 \subsection{Components and composition}
-\label{sec:components}
+\label{secn:components}
 
@@
 \end{definition}
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=\columnwidth]{BIPspec-ArchFailureTimerMax-v3}
+  \caption{The BIP specification of the Failure Monitor architecture}
+  \label{fig:schema:ArchFailure:BIP}
+\end{figure}
+
+In this paper, we will use a running example, which is a refined
+version of the Failure Monitor architecture
+from~\cite{CubETH-case-study}.  Although \fig{schema:ArchFailure:BIP}
+shows the full definition of this architecture, we will explain its
+various elements progressively, as we define the corresponding
+notions.
+
+The model in \fig{schema:ArchFailure:BIP} has three components.  The
+component $\NameOprnd$ is an \emph{operand} of the architecture, \ie
+it only has its interface defined: $(\emptyset, \{\PortFinish,
+\PortResume, \PortFail\}, \export[\emptyset])$, with
+$\export[\emptyset](p) = \emptyset$, for all $p \in \{\PortFinish,
+\PortResume, \PortFail\}$.  The other two components, $\NameCtrl$ and
+$\NameTimer$, are \emph{coordinators}\mdash they are specified
+completely, including the states and transitions defining their
+\emph{behaviour}.  Transitions are labelled with the ports of the
+corresponding components, Boolean guards and update functions on local
+variables.  For instance the loop transition $\tstate{1}
+\goesto{\PortTick, \GuardTick[], \TimerUpd[]} \tstate{1}$ in the
+$\NameTimer$ component is labeled by the port $\PortTick$, it can be
+fired only when the current value of the local variable $t$ is less
+than $z.u$, where $z = [l, u]$ is a local variable representing an
+interval.  Upon firing, this transition decrements the value of $t$ by
+$1$.  The guard and update function of the transition $\tstate{1}
+\goesto{\PortResume} \tstate{0}$ are omitted.  The default values are
+the constant predicate $\true$ and the $\mathit{skip}$ operator
+respectively.  The initial valuations $\val{0}{\NameTimer} = \{z
+\mapsto [0,0], t \mapsto 0\}$ and $\val{0}{\NameCtrl} =
+\{\mathit{zone} \mapsto [\mathrm{Min}, \mathrm{Max}]\}$ are shown by
+initialising transitions $\goesto{\TimerInitZone[]} \tstate{0}$ and
+$\goesto{\IntervalInit[]} \cstate{0}$ respectively.  The constants
+$\mathrm{Min}$ and $\mathrm{Max}$ are the parameters of the
+architecture.
+%\noteLH{It looks like Max is in zone, I do not understand}
+
+\todoSBin{Speak of guard monotonicity}
 
@@
 %
-  For a set of ports $a \subseteq P$, we denote $\supp{a}
-  \bydef{=} \setdef{i \in I}{a \cap P_i \neq \emptyset}$ the
-  \emph{support} of $a$.
   %% \noteSB{Updated this}\hl{and $V_a \bydef{=} \bigcup_{i \in
@@
 \end{definition}
+
+%% \noteLH{supp should go outside the definition}
+When speaking of a set of components or interfaces , we will always
+assume that it satisfies the disjointness assumption of \defn{im}.
+%
+We call the \emph{support} of a set of ports $a \subseteq P$, denoted
+$\supp{a}$, either the set $\setdef{i \in I}{a \cap P_i \neq
+  \emptyset}$ (for $P = \bigcup_{i=1}^n P_i$) or the set $\setdef{B
+  \in \cB}{a \cap P_B \neq \emptyset}$ (for $P = \bigcup_{B \in \cB}
+P_B$).  The precise meaning of this notation will always be clear from
+the context.  Intuitively, for an interaction $(a, g, e)$, $\supp{a}$
+denotes the set of the participating components.
 
@@
 
-Below, when speaking of a set of components $\cB$ or interfaces, we will always
-assume that it satisfies the disjointness assumption of \defn{im}.
-%
-For a set of ports $a$, we will abuse the notation by writing
-$\supp{a}$ to also denote the set $\setdef{B \in \cB}{a \cap P_B
-  \neq \emptyset}$.  The precise meaning of this notation will
-always be clear from the context.
+Specifying interaction models as sets of sets of ports is not
+practical due to their potentially exponential size.  An algebra of
+connectors was introduced in \cite{BliSif08-acp-tc} in order to
+structure interactions in BIP models.
+
+Connectors are hierarchical, tree-like structures with component ports
+at the leaves.  They define sets of interactions, based on the
+attributes of the connected ports, which may be either \emph{trigger}
+(triangles in \fig{schema:ArchFailure:BIP}) or \emph{synchron}
+(bullets in \fig{schema:ArchFailure:BIP}).
+%
+If all sub-connectors of a connector are synchrons, then an
+interaction may be executed by the connector only if each subconnector
+can contribute.
+%
+If at least one of the sub-connectors is a trigger, then any
+interaction consisting of contributions of any set of sub-connectors,
+\emph{involving at least one of the triggers}, can be executed.
+The composition semantics of BIP systems consists in
+firing exactly one interaction, enabled through at least one of the
+top-level connectors, at each execution round.
+
+For instance, in \fig{schema:ArchFailure:BIP}, the two ports
+$\NameTimer.\PortStart$ and $\NameCtrl.\PortFail$ are always
+synchronised, since they belong to the same binary sub-connector,
+where they are both synchrons.  In particular, this means that
+whenever the transition $\cstate{0} \goesto{\PortFail} \cstate{1}$ is
+fired, so is the transition $\tstate{0} \goesto{\PortStart,
+  \TimerInit[]} \tstate{1}$, initialising the timer.  The binary
+connector $\NameTimer.\PortStart \bullet\!\!\!-\!\!\!-\!\!\!\bullet
+\NameCtrl.\PortFail$ is a sub-connector of a hierarchical connector,
+where the port $\NameOprnd.\PortFail$ is a trigger.  Thus, the above
+interaction can only happen together with $\NameOprnd.\PortFail$,
+forming a ternary interaction.  On the contrary, being a trigger, the
+port $\NameOprnd.\PortFail$ can fire alone, forming a singleton
+interaction.
+
+\todoSBin{Speak of data transfer}
+
+\todoSBin{Provide the interaction model}
 
@@
 
+%% Finally, \emph{priorities}\mdash defined by a strict partial order on
+%% the set of possible interactions\mdash narrow the choice among the
+%% enabled interactions at any given round.  The default priority is the
+%% so-called \emph{maximal progress}, whereby among any two interactions
+%% $a \subset b$ (as sets of ports), $b$ has higher priority than $a$.
+Going back to our running example in \fig{schema:ArchFailure:BIP}, the
+port $\NameOprnd.\PortFail$ will never fire alone in a global state,
+where both $\NameTimer.\PortStart$ and $\NameCtrl.\PortFail$ are
+enabled.
+
+%% Adding priorities $\NameOprnd.\PortFinish < \NameCtrl.\PortReset$ and
+%% $\NameOprnd.\PortFinish < \NameOprnd.\PortResume$, ensures that, after
+%% a failure, the operation performed by $\NameOprnd$ cannot finish
+%% unless it is explicitly resumed or the system is reset.
+
 \begin{note}
@@
 
-%****************************************************************
-\subsection{Running example: Failure Monitor architecture}
-\label{secn:failure-monitor}
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=\columnwidth]{BIPspec-ArchFailureTimerMax-v3}
-  \caption{The BIP specification of the Failure Monitor architecture}
-  \label{schema:ArchFailure:BIP}
-\end{figure}
-
-Figure~\ref{schema:ArchFailure:BIP} shows a refined version of the
-Failure Monitor architecture used in~\cite{CubETH-case-study}.
+%% %****************************************************************
+%% \subsection{Running example: Failure Monitor architecture}
+%% \label{secn:failure-monitor}
+
+%\noteLH{Ludo ou simon: essayer de remonter la description generique en debut de section}
+
+%****************************************************************
+\subsection{Architectures}
+\label{secn:archi}
+
+\todoSBin{Sort out the following two paragraphs}
+
 Contrary to standard BIP models, architectures comprise one or several
@@
 consists of the ports $\PortFinish$, $\PortResume$ and $\PortFail$.
-The two \emph{coordinator} components\mdash $\NameCtrl$ and
-$\NameTimer$\mdash are standard BIP components insofar as they also
-have their \emph{behaviour} specified by finite automata extended with
-local data variables.  Transitions of these automata are labelled with
-the ports of the corresponding components, Boolean guards and update
-functions on local variables.  For instance the loop transition
-$\tstate{1} \goesto{\PortTick, \GuardTick[], \TimerUpd[]} \tstate{1}$
-in the $\NameTimer$ component is labeled by the port $\PortTick$, it
-can be fired only when the current value of the local variable $t$ is
-greater than $0$.  Upon firing, this transition decrements the value
-of $t$ by $1$.  When omitted, the default guard (\resp update
-function) is the constant predicate $\true$ (\resp the $\mathit{skip}$
-operator).  The constant $\mathrm{Max}$, in $\tstate{0}
-\goesto{\PortStart, \TimerInit[]} \tstate{1}$, is a parameter of the
-architecture.\noteLH{It looks like Max is in zone, I do not understand}
-
-Connectors are hierarchical, tree-like structures with component ports
-at the leaves.  They define sets of \emph{interactions}, based on the
-attributes of the connected ports~\cite{BliSif08-acp-tc}, which may be
-either \emph{trigger} (triangles in Fig.~\ref{schema:ArchFailure:BIP})
-or \emph{synchron} (bullets in Fig.~\ref{schema:ArchFailure:BIP}).
-%
-If all sub-connectors of a connector are synchrons, then an
-interaction may be executed by the connector only if each subconnector
-can contribute.
-%
-If at least one of the sub-connectors is a trigger, then any
-interaction consisting of contributions of any set of sub-connectors,
-\emph{involving at least one of the triggers}, can be executed.
-%
-For instance, the two ports $\NameTimer.\PortStart$ and
-$\NameCtrl.\PortFail$ are always synchronised, since they belong to
-the same binary sub-connector, where they are both synchrons.  In
-particular, this means that whenever the transition $\cstate{0}
-\goesto{\PortFail} \cstate{1}$ is fired, so is the transition
-$\tstate{0} \goesto{\PortStart, \TimerInit[]} \tstate{1}$,
-initialising the timer.  The binary connector $\NameTimer.\PortStart
-\bullet\!\!\!-\!\!\!-\!\!\!\bullet \NameCtrl.\PortFail$ is a
-sub-connector of a hierarchical connector, where the port
-$\NameOprnd.\PortFail$ is a trigger.  Thus, the above interaction can
-only happen together with $\NameOprnd.\PortFail$, forming a
-ternary interaction.  On the contrary, being a trigger, the port
-$\NameOprnd.\PortFail$ can fire alone, forming a singleton
-interaction.  The composition semantics of BIP systems consists in
-firing exactly one interaction, enabled through at least one of the
-top-level connectors, at each execution round.
-
-Finally, \emph{priorities}\mdash defined by a strict partial order on
-the set of possible interactions\mdash narrow the choice among the
-enabled interactions at any given round.  The default priority is the
-so-called \emph{maximal progress}, whereby among any two interactions
-$a \subset b$ (as sets of ports), $b$ has higher priority than $a$.
-For example, the port $\NameOprnd.\PortFail$ will never fire alone in
-a global state, where both $\NameTimer.\PortStart$ and
-$\NameCtrl.\PortFail$ are enabled.
-%
-%% Adding priorities $\NameOprnd.\PortFinish < \NameCtrl.\PortReset$ and
-%% $\NameOprnd.\PortFinish < \NameOprnd.\PortResume$, ensures that, after
-%% a failure, the operation performed by $\NameOprnd$ cannot finish
-%% unless it is explicitly resumed or the system is reset.
 
@@
 units (more details in Sect.~\ref{section:resultOA}).
-
-%****************************************************************
-\subsection{Architectures}
-\label{secn:archi}
 
@@
 	over the different variables of the
-	terms, labels, and states $s_i$, $\beta_j$, $s$, $\alpha$. $\Post\in 
+	terms, labels, and states  $\beta_j$, $s$, $\alpha$. $\Post\in 
 	\assigns{\variables}$\ is 
@@
 
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=\columnwidth]{FailureTimerZonePNET}
+  \caption{The pNET encoding the Failure Monitor architecture}
+  \label{schema:ArchFailure:BIP}
+\end{figure}
+
 %****************************************************************

### 2018-05-24 2017-Xudong-SMT/AVOCS-2018-pre-proceeding.tex
Modify the pre-proceeding paper.
Chang and remove the reference of the appendix.
Add the reference of RR in biblio.bib.

@@
  A full output of 
-the use-case is provided in appendice~\ref{appendix:fullOutput}.
+the use-case is provided in ~\cite{RR}.
 
@@
 \cite{henrio:Forte2016}, in the form of 2 structural rules, one for
-pLTSs, one for pNet nodes.  For convenience we also include these rules in
-App.~\ref{appendix:semRules}.
+pLTSs, one for pNet nodes. These rules are improved, adding guards in the synchronisation vectors and quantifier in the guards, in ~\cite{RR}.
 
@@
 When applied to a pLTSs at the leaves, we simply take the pLTS transitions of the
-corresponding local state and use the semantic rule (see TR1 in
-App.~\ref{appendix:semRules}) to build the OT.\footnote{%
+corresponding local state and use the semantic rule to build the OT.\footnote{%
 %
@@
 The \emph{Matching} method builds the OTs of a pNet node from those of
-its subnets (see rule Tr2 in App.~\ref{appendix:semRules}).
+its subnets.
 For each synchronisation vector and each possible
@@
 particular because of structured names for the fresh variables generated
-by the algorithm, allowing tracability of the result (see
-appendix~\ref{appendix:variables}).
+by the algorithm, allowing tracability of the result~\cite{RR}.
 
@@
 \emph{Translation of action algebra presentation.}
-In Appendix~\ref{appendix:mapsmt}, we  define the condition of
+In~\cite{RR}, we  define the condition of
 well-formedness of an algebra presentation, and its translation into
@@
 \emph{Translation of open transitions.}
-In App.~\ref{appendix:mapsmt} we formally define all steps of the translation of each
+In~\cite{RR} we formally define all steps of the translation of each
 open transition, including:
@@
 %
-Notice, however that the loop transitions
-$\underline{\mathit{resume}}$ in states $\ostate{s0,t0}$ and
-$\ostate{s2,t0}$, corresponding, respectively, to open transitions
-$ot_2$ and $ot_9$ in Fig.~\ref{schema:ots} of
-App.~\ref{appendix:fullOutput}, involve $\OTvar{resume(false)}$ from
-the two pLTS, \ie only the hole, corresponding to the operand
-component of the Failure Monitor architecture, executes $\PortResume$.
+%Notice, however that the loop transitions
+%$\underline{\mathit{resume}}$ in states $\ostate{s0,t0}$ and
+%$\ostate{s2,t0}$, corresponding, respectively, to open transitions
+%$ot_2$ and $ot_9$ in Fig.~\ref{schema:ots} of
+%App.~\ref{appendix:fullOutput}, involve $\OTvar{resume(false)}$ from
+%the two pLTS, \ie only the hole, corresponding to the operand
+%component of the Failure Monitor architecture, executes $\PortResume$.
 
@@
 in term of computing time. We tried a
-slighly bigger example, assembling 2 Failure controllers. In
-appendix~\ref{appendix:scalingup}, we show that Z3 can check the
+slighly bigger example, assembling 2 Failure controllers. In~\cite{RR}, we show that Z3 can check the
 satisfiablility of a 90K open transitions in a couple of minutes.

### 2018-05-25 2016-Weak-FH-Bisim/WeakBisim.tex
Ludo: Task 1,2,3 (improved def and 2 new properties)

@@
 \begin{definition}[Non-observability of silent actions]
-An open automaton $A = <J,\mathcal{S},s_0,\mathcal{T}>$ \emph{cannot observe silent actions} if and only if for all $j$ in $J$ we have
+An open automaton $A = <J,\mathcal{S},s_0,\mathcal{T}>$ \emph{cannot observe silent actions} if and only if for all $j$ in $J$ and $s$ in $\mathcal{S}$ we have
 \[ \openrule
@@
 \]
+and for all $\alpha$, $j$, $s$, $\Post$ and $s'$ we have
+\[ \openrule
+         {
+           (j\mapsto\tau),\Pred,\Post}
+         {s \OTarrow {\alpha} s'}
+         \in \mathcal{T} \implies \alpha=\tau\land s=s'\land \Post=\symb{Id}(s)
+\]
 \end{definition}
+
+We then have the following property that justifies the fact that we can abstract away tau transitions from holes.
+
+\begin{property}
+There is an open transition from state $s$ to state $s'$ if and only if there is a sequence of open transitions from $s$ to $s'$ where all open transitions except one are of the form:\[ \openrule
+         {
+           (j\mapsto\tau),\symb{True},\symb{Id}(s)}
+         {s \OTarrow {\tau} s}
+\]
+\end{property}
+\TODO{the formal view is not much interesting}
 
@@
 
+\begin{property}[Weak open transition transitivity]
+Let $A$ be an open automaton, and $<J,\mathcal{S},s_0,\WT>$ a weak open automaton derived from $A$.
+Suppose we have the following weak open transitions in $\WT$:
+\[\openrule
+         {
+           \overline{\gamma_1},\Pred_1,\Post_1   }
+         {s \OTWeakarrow {\tau} s_1}
+\qquad 
+\openrule
+         {
+           \overline{\gamma_2},\Pred_2,\Post_2   }
+         {s_1 \OTWeakarrow {\alpha} s_2}
+\qquad
+\openrule
+         {
+           \overline{\gamma_3},\Pred_3,\Post_3   }
+         {s_2 \OTWeakarrow {\tau} s_3}
+\]
+Then there is ag weak  open transition of the following form in $\WT$:
+\[\openrule
+         {
+           \overline{\gamma},\Pred,\Post   }
+         {s \OTWeakarrow {\alpha} s_3}
+\]
+Suppose additionally $\Post_3=({x_k\gets e_k})^{k\in K}$, we have the following
+\[
+\begin{array}{rcl}
+\gamma&=& \gamma_1\dotcup\gamma_2\dotcup\gamma_3\\
+\Pred&=&\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}\\
+\Post &=& ({x_k\gets ((e_k\subst{\Post_2})\subst{\Post_1})})^{k\in K}
+\end{array}\]
+\end{property}
+
 \TODO{We will discuss this corollary and the title.}
-
+\TODO{Move the following propertiesafter the definition of Weak bisim!}
 \begin{corollary}[Weak Composability]

### 2018-05-26 2017-Xudong-SMT/AVOCS-2018-pre-proceeding.tex
Hide the appendix in pre-proceeding.
Improve the pre-proceeding paper.

@@
 discharge some subgoals in the proofs.
-Tools like Rodin~\cite{deharbe2013,deharbe2014,abrial2007} have
+Tools like Rodin~\cite{deharbe2013,deharbe2014} have
 already integrated several provers, like Z3, as modules for proving
@@
 alternative to Z3, such as CVC4~\cite{barrett:CAV2011},
-Coq~\cite{armand:CPP2011},
-Isabelle~\cite{blanchette:FroCoS2011} or others.
+Coq~\cite{armand:CPP2011} or others.
 
@@
  A full output of 
-the use-case is provided in ~\cite{RR}.
+the use-case is provided in~\cite{Avocs-RR}.
 
@@
 \cite{henrio:Forte2016}, in the form of 2 structural rules, one for
-pLTSs, one for pNet nodes. These rules are improved, adding guards in the synchronisation vectors and quantifier in the guards, in ~\cite{RR}.
+pLTSs, one for pNet nodes. These rules are slightly improved, adding guards in the synchronisation vectors and syntax for universal quantifier in the guards (see~\cite{Avocs-RR}).
 
@@
 When applied to a pLTSs at the leaves, we simply take the pLTS transitions of the
-corresponding local state and use the semantic rule to build the OT.\footnote{%
+corresponding local state and use the semantic rule to build the OT\footnote{%
 %
@@
 %
-}
+}.
 When applied to a pNet node we use two methods, combining and
@@
 particular because of structured names for the fresh variables generated
-by the algorithm, allowing tracability of the result~\cite{RR}.
+by the algorithm, allowing tracability of the result~\cite{Avocs-RR}.
 
@@
 \emph{Translation of action algebra presentation.}
-In~\cite{RR}, we  define the condition of
-well-formedness of an algebra presentation, and its translation into
+In~\cite{Avocs-RR}, we  define the translation of an algebra presentation into
 SMTlib declarations (\texttt{declare-datatypes} and
-\texttt{declare-fun}). It ensures that the generated code is correct,
+\texttt{declare-fun}). We also formalize a condition of well-formedness of pNets ensures that the generated code is correct,
 and will not raise runtime errors in the SMT engine. Note that the
@@
 \emph{Translation of open transitions.}
-In~\cite{RR} we formally define all steps of the translation of each
+In~\cite{Avocs-RR} we formally define all steps of the translation of each
 open transition, including:
@@
 in term of computing time. We tried a
-slighly bigger example, assembling 2 Failure controllers. In~\cite{RR}, we show that Z3 can check the
+slighly bigger example, assembling 2 Failure controllers. In~\cite{Avocs-RR}, we show that Z3 can check the
 satisfiablility of a 90K open transitions in a couple of minutes.
@@
 
-\newpage
-\appendix
+\end{document}
+
+%\newpage
+%\appendix
 %\section{Appendix}
@@
 
-\end{document}
-
 \subsection{Simplification of Predicates}

### 2018-06-12 2016-Weak-FH-Bisim/WeakBisim.tex
weak bisi

@@
 
+\RAB{We let $\gamma$ range over sets of words and use $\dotcup$ as the union that appends sets of words.}
+
 We let $\gamma$ range over lists of action terms and use $\dotcup$ as the union that appends lists of action terms \TODO{write this properly}. $[a]$ is a list with a single element.
@@
 \end{theorem}
+
+\RAB{Weak bisimularity can be checked by reducing it to strong bisimularity. For this, we need to added in Definition \ref{def:buildweakOT} the following rule: }
+
+\begin{mathpar}
+  \mprset {vskip=.5ex}
+\inferrule{
+ \openrule
+         {
+           \overline{\beta},\Pred,\Post}
+         {s \OTarrow {\tau} s'} \in \mathcal{T}
+}
+{ \openrule
+         {
+           \vis{\overline{\beta}}\!,\Pred,\Post
+				 } {s \OTWeakarrow {\tau} s''} \in \WT
+}
+ \end{mathpar}
+\RAB{Given an open automaton  $A$, we can built a weak open automaton, denoted $A^{\omega}$, from rules given in Definition \ref{def:buildweakOT}.
+So weak bisimularity on $A$ coincides with strong bisimularity on $A^{\omega}$, than we can prove weak bisimularity with strong bisimularity on $A^{\omega}$.}
 

### 2018-06-13 2016-Weak-FH-Bisim/WeakBisim.tex
minor change in todo
changement reu 13/6

--- 2018-05-25 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
+INtiuition: tau is non observable if the automaton allows any tau transition from holes, and the global transition resulting from a tau in a hole is a tau transition not changing the action state.
 \TODO{Id(s) is the identity function on variables of state s}
@@
 An open automaton $A = <J,\mathcal{S},s_0,\mathcal{T}>$ \emph{cannot observe silent actions} if and only if for all $j$ in $J$ and $s$ in $\mathcal{S}$ we have
+\begin{enumerate}
+\item
 \[ \openrule
@@
 \]
-and for all $\alpha$, $j$, $s$, $\Post$ and $s'$ we have
+and 
+\item for all $\alpha$, $j$, $s$, $\Post$ and $s'$ such that
 \[ \openrule
@@
          {s \OTarrow {\alpha} s'}
-         \in \mathcal{T} \implies \alpha=\tau\land s=s'\land \Post=\symb{Id}(s)
+         \in \mathcal{T} \] we have \[ \alpha=\tau\land s=s'\land \Post=\symb{Id}(s)
 \]
+\end{enumerate}
 \end{definition}
 
-We then have the following property that justifies the fact that we can abstract away tau transitions from holes.
-
-\begin{property}
-There is an open transition from state $s$ to state $s'$ if and only if there is a sequence of open transitions from $s$ to $s'$ where all open transitions except one are of the form:\[ \openrule
-         {
-           (j\mapsto\tau),\symb{True},\symb{Id}(s)}
-         {s \OTarrow {\tau} s}
-\]
-\end{property}
-\TODO{the formal view is not much interesting}
+We then can add any number of $\tau$ transitions of the holes before or after any open transition freely.
+This property justifies the fact that we can abstract away $\tau$ transitions from holes in the definition of a weak open transition.
 
@@
 \def\InvAct{\mathcal{Inv}}
+
+\RAB{We let $\gamma$ range over sets of words and use $\dotcup$ as the union that appends sets of words.}
 
@@
 
-\noindent{\bf Invisible $\tau$ transitions:}
+%\noindent{\bf Invisible $\tau$ transitions:}
 \begin{mathpar}
@@
            \overline{\beta},\Pred,\Post}
-         {s \OTarrow {\tau} s'} \in \mathcal{T}
-\\
- \openrule
-         {
-           \overline{\gamma},\Pred\,',({x_k\gets e_k})^{k\in K}   }
-         {s' \OTWeakarrow {\tau} s''} \in \WT
+         {s \OTarrow {\alpha} s'} \in \mathcal{T}
 }
@@
          {
-           \vis{\overline{\beta}}\dotcup\overline{\gamma},\Pred\land\Pred\,'\subst{\Post\,},
-				({x_k\gets (e_k\subst{\Post\,})})^{k\in K} } 
-         {s \OTWeakarrow {\tau} s''} \in \WT
-}
+           \vis{\overline{\beta}}\!,\Pred,\Post
+				 } {s \OTWeakarrow {\alpha} s''} \in \WT
+}
+%\inferrule{
+% \openrule
+%         {
+%           \overline{\beta},\Pred,\Post}
+%         {s \OTarrow {\tau} s'} \in \mathcal{T}
+%\\
+% \openrule
+%         {
+%           \overline{\gamma},\Pred\,',({x_k\gets e_k})^{k\in K}   }
+%         {s' \OTWeakarrow {\tau} s''} \in \WT
+%}
+%{ \openrule
+%         {
+%           \vis{\overline{\beta}}\dotcup\overline{\gamma},\Pred\land\Pred\,'\subst{\Post\,},
+%				({x_k\gets (e_k\subst{\Post\,})})^{k\in K} } 
+%         {s \OTWeakarrow {\tau} s''} \in \WT
+%}
  \end{mathpar}
-
-\noindent{\bf Other transitions:}
+and
+%\noindent{\bf Other transitions:}
 \begin{mathpar}
@@
          {s \OTWeakarrow {\tau} s_1} \in \WT
-\qquad\qquad
+\qquad
 \openrule
          {
-           \overline{\beta},\Pred_2,\Post_2  }
-         {s_1 \OTarrow {\alpha} s_2} \in \mathcal{T}
-\\
+           \overline{\gamma_2},\Pred_2,\Post_2  }
+         {s_1 \OTWeakarrow {\alpha} s_2} \in \WT
+\qquad
 \openrule
@@
          {
-           \overline{\gamma_1}\dotcup \vis{\overline{\beta}}\dotcup\overline{\gamma_3},
+           \overline{\gamma_1}\dotcup \overline{\gamma_2}\dotcup\overline{\gamma_3},
 		\Pred,
@@
 
-\begin{theorem}[Weak FH-Bisimulation is an equivalence]\label{thm-weak-equiv} Suppose $\mathcal{R}$ 
-is a weak FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
-reflexive, symmetric and transitive.
-\end{theorem}
+\TODO{the formal view is not much interesting}
 
@@
 
+\subsection{Weak FH-bisimulation}
+
+\begin{definition}[Weak FH-bisimulation]\label{def-Weak-bisim}
+
+\noindent
+Let $A_1 = <J,\mathcal{S}_1, s_0,
+    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata.
+Let $<J,\mathcal{S}_1, s_0,
+    \WT_1>$ and $<J,\mathcal{S}_2,t_0,  \WT_2>$ be the
+weak open automata derived from $A_1$ and $A_2$ respectively.
+Let $\mathcal{R}$ a relation over
+$\mathcal{S}_1$ and $\mathcal{S}_2$, as in Definition~\ref{def-FH-bisim}.
+
+Then 
+   $\mathcal{R}$ is a weak FH-bisimulation iff for any  states
+$s\in\mathcal{S}_1$ and
+$t\in\mathcal{S}_2$ such that $(s,t|\Pred)\in\mathcal{R}$, we 
+   have the following:
+
+ \begin{itemize}
+ \item  For any open transition $OT$ in $\mathcal{T}_1$:
+ \begin{mathpar}
+     \openrule
+         {
+           \beta_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
+         {s \OTarrow {\alpha} s'}
+
+\end{mathpar}
+ there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
+ \begin{mathpar}
+    \openrule
+         {
+           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {t \OTWeakarrow {\alpha_x} t_x}
+\end{mathpar}
+ such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
+ and  \\
+ $\Pred \land \Pred_{OT}\\
+\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
+   \left( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
+     \land \alpha\!=\!\alpha_x \land  
+     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
+
+ \item  and symmetrically any open transition from $t$ in $\mathcal{T}_2$ can be 
+      covered by a set of weak transitions from $s$ in $\WT_1$.
+ \end{itemize}
+
+Two pNets are Weak FH-bisimilar if there exist a relation between their associated 
+automata that is a Weak FH-bisimulation and their initial states are in the relation, i.e. 
+the predicate associated to the relation between the initial states is true.
+ \end{definition}
+
+Weak bisimulation can be alternatively defined as a strong bisimulation on the weak open automata, however this would still need a specific definition of strong bisimulation for weau open automata.
+\TODO{polish}
+
+\begin{theorem}[Weak FH-Bisimulation is an equivalence]\label{thm-weak-equiv} Suppose $\mathcal{R}$ 
+is a weak FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
+reflexive, symmetric and transitive.
+\end{theorem}
+
+\subsection{Weak bisimulation for open pNets}
+\begin{definition}[Non-observability of silent actions]~\\
+A pNet $\mylangle \pNet_i^{i\in I} , \Sort_j^{j\in J}, \overline{\symb{SV}}\myrangle$
+ \emph{cannot observe silent actions} if it verifies:\\ $\forall i\in I\uplus J.\, \SV{(i\mapsto \tau)}{\tau}{\symb{True}}\in \overline{\symb{SV}}$ and $\forall i,j\in I\uplus J.\,i\neq j \Rightarrow \alpha_i\neq\tau$
+\end{definition}
+
+\begin{property}[pNets that cannot observe silent actions]
+The open semantics of a pNets that cannot observe silent actions is an open automaton that  cannot observe silent actions.
+\end{property}
+
+\begin{property}[Decomposition of weak open transitions] \TODO{TODO}
+Let $A$ be the open automaton that is the semantics of a \pNet $P$, and $<J,\mathcal{S},s_0,\WT>$ a weak open automaton derived from $A$.
+Suppose we have the following weak open transitions in $\WT$:
+\[\openrule
+         {
+           \overline{\gamma_1},\Pred_1,\Post_1   }
+         {s \OTWeakarrow {\tau} s_1}
+\qquad 
+\openrule
+         {
+           \overline{\gamma_2},\Pred_2,\Post_2   }
+         {s_1 \OTWeakarrow {\alpha} s_2}
+\qquad
+\openrule
+         {
+           \overline{\gamma_3},\Pred_3,\Post_3   }
+         {s_2 \OTWeakarrow {\tau} s_3}
+\]
+Then there is ag weak  open transition of the following form in $\WT$:
+\[\openrule
+         {
+           \overline{\gamma},\Pred,\Post   }
+         {s \OTWeakarrow {\alpha} s_3}
+\]
+Suppose additionally $\Post_3=({x_k\gets e_k})^{k\in K}$, we have the following
+\[
+\begin{array}{rcl}
+\gamma&=& \gamma_1\dotcup\gamma_2\dotcup\gamma_3\\
+\Pred&=&\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}\\
+\Post &=& ({x_k\gets ((e_k\subst{\Post_2})\subst{\Post_1})})^{k\in K}
+\end{array}\]
+\end{property}
+
 \TODO{We will discuss this corollary and the title.}
-\TODO{Move the following propertiesafter the definition of Weak bisim!}
 \begin{corollary}[Weak Composability]
@@
 \end{corollary}
-
-\subsection{Non-observability and open pNets}
-\begin{definition}[Non-observability of silent actions]~\\
-A pNet $\mylangle \pNet_i^{i\in I} , \Sort_j^{j\in J}, \overline{\symb{SV}}\myrangle$
- \emph{cannot observe silent actions} if it verifies:\\ $\forall i\in I\uplus J.\, \SV{(i\mapsto \tau)}{\tau}{\symb{True}}\in \overline{\symb{SV}}$ and $\forall i,j\in I\uplus J.\,i\neq j \Rightarrow \alpha_i\neq\tau$
-\end{definition}
-
-\begin{property}[pNets that cannot observe silent actions]
-The open semantics of a pNets that cannot observe silent actions is an open automaton that  cannot observe silent actions.
-\end{property}
 
@@
 %% Note that
-
-\begin{definition}[Weak FH-bisimulation]\label{def-Weak-bisim}
-
-\noindent
-Let $A_1 = <J,\mathcal{S}_1, s_0,
-    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata.
-Let $<J,\mathcal{S}_1, s_0,
-    \WT_1>$ and $<J,\mathcal{S}_2,t_0,  \WT_2>$ be the
-weak open automata derived from $A_1$ and $A_2$ respectively.
-Let $\mathcal{R}$ a relation over
-$\mathcal{S}_1$ and $\mathcal{S}_2$, as in Definition~\ref{def-FH-bisim}.
-
-Then 
-   $\mathcal{R}$ is a weak FH-bisimulation iff for any  states
-$s\in\mathcal{S}_1$ and
-$t\in\mathcal{S}_2$ such that $(s,t|\Pred)\in\mathcal{R}$, we 
-   have the following:
-
- \begin{itemize}
- \item  For any open transition $OT$ in $\mathcal{T}_1$:
- \begin{mathpar}
-     \openrule
-         {
-           \beta_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
-         {s \OTarrow {\alpha} s'}
-
-\end{mathpar}
- there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {t \OTWeakarrow {\alpha_x} t_x}
-\end{mathpar}
- such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
- and  \\
- $\Pred \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-   \left( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
-     \land \alpha\!=\!\alpha_x \land  
-     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
-
- \item  and symmetrically any open transition from $t$ in $\mathcal{T}_2$ can be 
-      covered by a set of weak transitions from $s$ in $\WT_1$.
- \end{itemize}
-
-Two pNets are Weak FH-bisimilar if there exist a relation between their associated 
-automata that is a Weak FH-bisimulation and their initial states are in the relation, i.e. 
-the predicate associated to the relation between the initial states is true.
- \end{definition}
 

### 2018-06-13 2017-Xudong-SMT/AVOCS-2018-RR-eric.tex
RR-version of the AVOCS paper.

--- 2018-05-24 2017-Xudong-SMT/AVOCS-2018-pre-proceeding.tex
@@
 
-\documentclass{lncs/llncs}
+\documentclass[twoside]{article}
+% \documentclass{lncs/llncs}
 \usepackage{etex}
-
-\usepackage[T1]{fontenc}
+\usepackage[a4paper]{geometry}
+\usepackage[latin1]{inputenc} % ou \usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc} % ou \usepackage[OT1]{fontenc}
+\usepackage{graphicx}
 % \usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
@@
 %\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
-\usepackage{graphicx}
 
@@
 
-%\newtheorem{theorem}{Theorem}[section]
+\newtheorem{theorem}{Theorem}[section]
 \newtheorem{prop}[theorem]{Proposition}
@@
 \newtheorem{alg}[theorem]{Algorithm}
-%\newtheorem{remark}[theorem]{Remark}
-%\newtheorem{definition}[theorem]{Definition}
-%\newtheorem{example}[theorem]{Example}
+\newtheorem{remark}[theorem]{Remark}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{example}[theorem]{Example}
 %\newtheorem{problem}[theorem]{Problem}
@@
 
-\title{Using SMT engine to generate Symbolic Automata\thanks{This work was partially 
-funded by the Associated Team FM4CPS
-  between INRIA and ECNU, Shanghai}}
-\author{ Xudong Qin\inst{1,2}  \ \ \  Simon Bliudze\inst{3} \ \ \ Eric Madelaine\inst{1}
-  \ \ \  Min Zhang\inst{2}} 
-\institute{Universit\'e C\^ote d'Azur, Inria, CNRS, I3S, 06902 Sophia Antipolis, France
-        \and Shanghai Key Laboratory of Trustworthy Computing, ECNU, China
-\and INRIA Lille -- Nord Europe, 40 avenue Halley,
-59650 Villeneuve d'Ascq,
-France}
-\date{}                                           % Activate to display a given date or no date
-
-                          % Activate to display a given date or no date
-
-\begin{document}
-
-\maketitle
-
-%\section{}
-%\subsection{}
-
-\begin{abstract}
-Open pNets are used to model the behaviour of open systems, both
+\usepackage{RR}
+\RRNo{0000}
+\RRdate{May 2018}
+\RRauthor{% les auteurs
+Xudong  \MakeUppercase{Qin}
+\thanks{MoE Engineering Research Center for Software/Hardware Co-design Technology and Application, East China Normal University, 200062, Shanghai, China}
+\and
+Simon \MakeUppercase{Bliudze}
+\thanks{INRIA Lille-Nord Europe, 40 avenue Halley, 59650 Villeneuve d'Asq, France}
+\and
+Eric \MakeUppercase{Madelaine}
+\thanks[inria]{INRIA Sophia Antipolis M\'editerran\'ee, BP 93, 06902 Sophia Antipolis, France}
+\and
+Min  \MakeUppercase{Zhang}
+\thanks{MoE Engineering Research Center for Software Hardware Co-design Technology and Application, East China Normal University, 200062, Shanghai, China}
+}
+
+%% Ceci apparait sur chaque page paire.
+\authorhead{Qin \& Bliudze \& Madelaine \& Zhang}
+
+\RRetitle{Using SMT engine to generate Symbolic Automata - Extended version}
+\RRtitle{Utilisation d'un Moteur SMT pour g\'en\'erer des Automates Symboliques- Version \'etendue}
+\titlehead{Using SMT engine to generate Symbolic Automata}
+
+\RRnote{KAIROS is a common team between the I3S Lab (Univ. of Nice
+  Sophia-Antipolis and CNRS) and INRIA Sophia Antipolis M\'editerran\'ee}
+
+\RRabstract{Open pNets are used to model the behaviour of open systems, both
 synchronous or asynchronous, expressed in various calculi or
@@
 behavioural properties; we give 2 examples, a safety and a liveness
-property.
-\end{abstract}
+property.}
+
+\RRresume{Les pNets ouverts sont utilisés pour modéliser le comportement des systèmes ouverts, synchrones ou asynchrones, exprimée dans divers calculs ou
+langages de programmation.
+Ils sont dotés d'une sémantique opérationnelle symbolique en termes d'«Automata Ouverts».
+Cela nous permet de vérifier les propriétés de ces systèmes d'une manière compositionnelle.
+Nous avons implémenté un algorithme calculant ces sémantiques,
+en construisant des prédicats exprimant les conditions de synchronisation
+entre les actions des composants du pNet. La vérification de tels
+prédicats nécessite un raisonnement symbolique sur les logiques de premier ordre, mais également sur des données spécifiques à l'application. Nous utilisons le moteur SMT Z3 pour vérifier la
+satisfiabilité des prédicats, et ne conserver dans l'automate ouvert que les
+transitions satisfiables.
+
+Nous illustrons notre approche par un exemple d'inspiration industrielle.
+Pour cela nous partons d'«architectures» de systèmes BIP, qui ont été utilisés dans le cadre d'un projet de l'Agence Spatiale Européenne pour spécifier le logiciel de contrôle d'un nanosatellite au Centre d'ingénierie spatiale de l'EPFL.
+Nous utilisons les pNets pour encoder une architecture BIP
+étendu avec des données explicites, et calculer sa
+sémantique en termes d'automates ouverts. Cet automate peut être utilisé pour prouver des 
+propriétés comportementales; nous donnons 2 exemples, une propriete de sureté et une de vivacité.}
+
+\RRmotcle{S\'emantique comportementale symbolique, Analyse compositionelle de logiciels, R\'eseaux d'automates synchronis\'es}
+\RRkeyword{Symbolic behavioral semantics, 
+Compositional analysis of software systems, 
+Networks of synchronized automata}
+\RRprojet{Kairos}
+%\RRprojetcommun{Scale}
+\RCSophia % Sophia Antipolis M\'editerran\'ee
+
+\begin{document}
+\makeRR
+
+%\section{}
+%\subsection{}
 
@@
 
-BIP
-(Behaviour-Interaction-Priority)~\cite{bip} is a framework for the
+BIP(Behaviour-Interaction-Priority)~\cite{bip} is a framework for the
 component-based design of concurrent software and systems.  In
@@
 $C = ({ot}_i)^{i \in [1,n]} \in \overline{comb}$, such that, for each $i \in [1,n]$, either $ot_i = -$, or the result action of $ot_i$ is $a_i$; the hole behaviours $\mathit{Hole} = (b_j)^{j \in J}$; and a fresh variable $v$, representing the result action of the OT under construction, we build the predicate:
-%
-\begin{multline*}
-  \mathit{MkPred}(sv, C, \overline{\mathit{hole}}) = 
-  \\
-  (\forall i\in I, a_i=a'_i) \land
-%  (\forall i \not\in I, ot_i = -) \land
+
+$$
+  \mathit{MkPred}(sv, C, \overline{\mathit{hole}})=(\forall i\in I, a_i=a'_i) \land
   (\forall j\in J, b_j=b'_j) \land
-  (v=v') \land G_k.
-\end{multline*}
+  (v=v') \land G_k
+$$
 
@@
 
-\begin{theorem}[Finiteness of open-automata.]\\
-Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
-  J}$, if the sets $L$ and $J$ are finite, if the synchronization vectors of all pNets 
+\begin{theorem}[Finiteness of open-automata.]
+Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in J}$, if the sets $L$ and $J$ are finite, if the synchronization vectors of all pNets
   included in  $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ 
@@
 The format of \emph{fresh variable} (renaming) is defined as:
-``$\emph{prefix : tree\ index\ :\ counter}$''.
+$$\emph{prefix : tree\ index\ :\ counter.}$$
 \begin{itemize}
@@
 
-\begin{table}\caption{\label{Table:predefinedSorts}\leftline{Algebra Presentation: predefined Sorts
-  and Operators}}
+\begin{table*}
+
+\begin{minipage}{\textwidth}
+	\caption{\label{Table:predefinedSorts}\leftline{Algebra Presentation: predefined Sorts and Operators}}
 	\begin{tabular}{p{3cm}p{3cm}p{6cm}}
@@
 	\end{tabular}
-\end{table}
-
-\begin{table}\caption{\label{table:BIPoperators}\leftline{Additional
-      operator for the BIP algebra}}
+	\vspace{12ex}
+\end{minipage}
+\begin{minipage}{\textwidth}
+\caption{\label{table:BIPoperators}\leftline{Additional operator for the BIP algebra}}
 	\begin{tabular}{p{3cm}p{3cm}p{6cm}}
@@
 	\end{tabular}
-\end{table}
+\vspace{12ex}
+\end{minipage} 
+\begin{minipage}{\textwidth}
+	\caption{\label{table:CCSalgebra}\leftline{Additional sorts and operators for the CCS algebra}}
+	\begin{tabular}{p{3cm}p{3cm}p{6cm}}
+		\hline\specialrule{0em}{1pt}{1pt}
+		Sort & Constructors & Auxiliary Operators
+                \\\specialrule{0em}{1pt}{1pt}
+		\hline\specialrule{0em}{3pt}{3pt}
+		Channel, Data    			&
+                $\emptyset$&
+                $\emptyset$
+                \\\specialrule{0em}{1pt}{1pt} 
+		Action 			&  $\texttt{Emit(c,v)},\texttt{Receive(c,v)},\texttt{Tau}$ &
+		\\\hline
+	\end{tabular}
+\end{minipage}
+
+\end{table*}
 
@@
 \end{example}
-
-\begin{table}\caption{\label{table:CCSalgebra}\leftline{Additional
-      sorts and operators for the CCS algebra}}
-	\begin{tabular}{p{3cm}p{3cm}p{6cm}}
-		\hline\specialrule{0em}{1pt}{1pt}
-		Sort & Constructors & Auxiliary Operators
-                \\\specialrule{0em}{1pt}{1pt}
-		\hline\specialrule{0em}{3pt}{3pt}
-		Channel, Data    			&
-                $\emptyset$&
-                $\emptyset$
-                \\\specialrule{0em}{1pt}{1pt} 
-		Action 			&  $\texttt{Emit(c,v)},\texttt{Receive(c,v)},\texttt{Tau}$ &
-		\\\hline
-	\end{tabular}
-\end{table}
 
@@
 SMT-LIB language (\cite{BarFT-RR-17}), but there are a number of differences in the
-structure of the models/languages, so the translation is not trivial.
+structure of the models languages, so the translation is not trivial.
 
@@
 
-\subsubsection{Presentation Translation} %\TODO{Duplicate ? no,
+\subsection{Presentation Translation} %\TODO{Duplicate ? no,
                                 %slightly more precise that in the
@@
 
-\begin{lstlisting}
+%\begin{lstlisting}
 Let Pres = <Sorts, Constrs, Ops> an extended presentation
@@
 using the following translation function:
-
-\end{lstlisting}
+\\
+%\end{lstlisting}
 
@@
 		\hline
+		\\
 \end{tabular}
@@
 
+\begin{table}
 \begin{example}
@@
  \end{example}
-
-\subsubsection{Predicate translation}
+ \vspace{25ex}
+\end{table}
+
+\subsection{Predicate translation}
 

### 2018-06-15 2017-Xudong-SMT/AVOCS-2018-RR-eric.tex
RR working version
fini

@@
 \usepackage{RR}
-\RRNo{0000}
-\RRdate{May 2018}
+\RRNo{9177}
+\RRdate{June 2018}
 \RRauthor{% les auteurs
-Xudong  \MakeUppercase{Qin}
-\thanks{MoE Engineering Research Center for Software/Hardware Co-design Technology and Application, East China Normal University, 200062, Shanghai, China}
+Xudong \MakeUppercase{Qin}\thanks[inria-sam]{Universit\'e C\^ote d'Azur, INRIA, CNRS, 06902 Sophia Antipolis, France}\thanks[ecnu]{Shanghai Key Laboratory for Trustworthy Computing, East China Normal University, Shanghai, China}
 \and
-Simon \MakeUppercase{Bliudze}
-\thanks{INRIA Lille-Nord Europe, 40 avenue Halley, 59650 Villeneuve d'Asq, France}
+Simon \MakeUppercase{Bliudze}\thanks{INRIA Lille-Nord Europe, 40 avenue Halley, 59650 Villeneuve d'Asq, France}
 \and
-Eric \MakeUppercase{Madelaine}
-\thanks[inria]{INRIA Sophia Antipolis M\'editerran\'ee, BP 93, 06902 Sophia Antipolis, France}
+Eric \MakeUppercase{Madelaine}\thanksref{inria-sam}
 \and
-Min  \MakeUppercase{Zhang}
-\thanks{MoE Engineering Research Center for Software Hardware Co-design Technology and Application, East China Normal University, 200062, Shanghai, China}
+Min \MakeUppercase{Zhang}\thanksref{ecnu}
+%\thanks{MoE Engineering Research Center for Software Hardware Co-design Technology and Application, East China Normal University, 200062, Shanghai, China}
 }
@@
 \RRnote{KAIROS is a common team between the I3S Lab (Univ. of Nice
-  Sophia-Antipolis and CNRS) and INRIA Sophia Antipolis M\'editerran\'ee}
+  Sophia-Antipolis and CNRS) and INRIA Sophia Antipolis M\'editerran\'ee.\\
+This work was partially funded by the Associated Team FM4CPS between Inria and ECNU Shanghai.}
 
@@
 
-\section{Introduction}
+\section{Introduction}\footnote{This Research Report is the extended version of the eponym paper presented at the 18th Int.
+Workshop on Automated Verification of Critical Systems (AVOCS'18) in Oxford, July 2018.}
 
@@
 unification  will be checked later, together with the guards collected
-from synchronisation vectors and from pLTS transtions, using the
+from synchronisation vectors and from pLTS transitions, using the
 satisfiability check in the SMT engine.
@@
 \subsection{Management of state variable assignments}
+\label{section:state-variables}
 
@@
 \subsection{Translation to SMTlib}
+\label{section:translation}
 
@@
 \emph{Translation of action algebra presentation.}
-In Appendix~\ref{appendix:mapsmt}, we  define the condition of
+In Appendix~\ref{appendix:well-formedness} and~\ref{appendix:mapsmt}, we  define the condition of
 well-formedness of an algebra presentation, and its translation into
@@
 Additionally, we will include axiomatisation of any required functions
-and predicates of the presentation data-types.
+and predicates of the algebra data-types.
 
@@
 The result (sat or unsat) of the final \texttt{check-sat} command in
-the translation () is then decoded.
+the translation is then decoded.
 
@@
 $ot_2$ and $ot_9$ in Fig.~\ref{schema:ots} of
-App.~\ref{appendix:fullOutput}, involve $\OTvar{resume(false)}$ from
+Appendix~\ref{appendix:fullOutput}, involve $\OTvar{resume(false)}$ from
 the two pLTS, \ie only the hole, corresponding to the operand
@@
 that in the state $\ostate{s2,t0}$ only the reset transition involves
-$\NameCtrl$.  Therefore, under resonable scheduling assumptions,
+$\NameCtrl$.  Therefore, under reasonable scheduling assumptions,
 $\PortReset$ will always be fired.
@@
 
-\emph{Scaling up.} One important motivation of this work is to
+\emph{Scaling up.} \label{paragraph:scalingup} One important motivation of this work is to
 attack the complexity of verification of realistic systems by a
@@
 %\section{Appendix}
-The following appendices are included for the convenience of reviewers.
-Our intention is to publish as a research report, before final publication, an
-extended version containing all technical details, proofs, and more examples.
-
-The appendices are organized in the following way:
+These appendices include details that were kept out of the original paper by lack of space.
+More precisely, they contain:
 
@@
 that were already published in \cite{henrio:Forte2016}.
+These rules are referenced from section \ref{section:implementation}, \pageref{section:implementation}, and implemented by the algorithms \ref{alg1} \& \ref{alg2}.
+Compared to the rules in \cite{henrio:Forte2016}, they were slightly extended to take into account guards in the synchronisation vectors.
 
@@
 
+  \medskip
   \begin{description}
@@
 management in the tool: the generation of variables names, and the
-management of state variable assignments.
+management of state variable assignments. These were described shortly
+in Section \ref{section:state-variables},\ref{section:translation}.
 
@@
     state $gs$
-  \item $Assigns(svar)$ the set of possible assignments of variable
+  \item $Assigns(svar)$ the set of possible assignments (= expressions) of variable
       $svar$.
@@
 in open transitions), we need to generate SMTlib programs, from the
-pNet Algebra presentation and predicates.
+pNet Algebra presentation and predicates. This is the first part of the
+translation introduced in section \ref{section:translation}.
 More precisely, we need to translate to SMTlib:
@@
 \section{Well-formness and typing of expressions}
+\label{appendix:well-formedness}
 
@@
 
-In this section we define separately
+In this section we define separately (as introduced in Section~\ref{section:translation}):
 \begin{itemize}
@@
 		&$Sorts \& Constructors \translate$	declare-datatypes				\\\specialrule{0em}{1pt}{1pt}
-		&$Other operators \lhook\joinrel\longrightarrow$	declare-function		\\\specialrule{0em}{1pt}{1pt}
+		&$Other operators \lhook\joinrel\longrightarrow$	declare-fun		\\\specialrule{0em}{1pt}{1pt}
 		(Open Transition)							
@@
  \end{example}
- \vspace{25ex}
+ \vspace{2ex}
 \end{table}
@@
 function, and $\longrightarrow$ the TrPredicate auxiliary function.
+\newpage
 
@@
 		\\
-		$\dfrac{Ass = \bigwedge\limits_{k\in K}(x_k, a_k)~~x_k\in SVar(gs)~~a_k = Assigns(x_k)}{Ass \translate \texttt{map} \translate (x_k, a_k)}$
+		$\dfrac{Ass = \bigwedge\limits_{k\in K}(x_k, a_k)~~x_k\in SVar(gs)~~a_k = Assigns(x_k)}{Ass \translate \texttt{ (map} \translate (x_k, a_k))}$
 		\\\specialrule{0em}{3pt}{3pt}		
-		$\dfrac{a_k = e_1,...,e_n}{(x_k, a_k) \translate \texttt{(assert (or (= }x_k\texttt{ map} \longrightarrow e_1\texttt{)}\texttt{...(= }x_k\texttt{ map} \longrightarrow e_n\texttt{)}  \texttt{))}}$
+		$\dfrac{a_k = e_1,...,e_n}{(x_k, a_k) \translate \texttt{(assert (or (= }x_k\texttt{ (map} \longrightarrow e_1\texttt{))}\texttt{...(= }x_k\texttt{ (map} \longrightarrow e_n\texttt{)}  \texttt{)))}}$
 		\\\specialrule{0em}{3pt}{3pt}\hline\specialrule{0em}{3pt}{5pt}
@@
 		\\\specialrule{0em}{3pt}{3pt}
-		$\dfrac{arg = op'(args)~~op'\in Constr~~arity(op')\neq 0}{op' \longrightarrow \texttt{(}name(op')~~map\longrightarrow args\texttt{)}}$
+		$\dfrac{arg = op'(args)~~op'\in Constr~~arity(op')\neq 0}{op' \longrightarrow \texttt{(}name(op')~~(map\longrightarrow args\texttt{))}}$
 		\\\specialrule{0em}{3pt}{3pt}
-		$\dfrac{arg = op'(args)~~op'\in Ops}{op' \longrightarrow \texttt{(}name(op')~~map\longrightarrow args\texttt{)}}$
+		$\dfrac{arg = op'(args)~~op'\in Ops}{op' \longrightarrow \texttt{(}name(op')~~(map\longrightarrow args\texttt{))}}$
 		\\\\\specialrule{0em}{1pt}{1pt}
@@
 
-\paragraph{properties}
+\paragraph{Properties:}
 The rules in the sections above are meant to guarantee that no runtime
@@
 The following listing contains the final list of OTs generated for our
-use-case. It is displayed in full and raw format, each OT containing
+use-case, as summarized in section~\ref{section:resultOA} page~\pageref{section:resultOA}. It is displayed in full and raw format, each OT containing
 in its premisses: the list of transitions of pLTSs and actions of
@@
 
+In our discussion~\pageref{paragraph:scalingup}, we mentionned an experiment done with a slightly larger example.
 We build a larger system by composing several subsystems. In the

### 2018-06-26 2016-Weak-FH-Bisim/WeakBisim.tex
proof of weak bisim

@@
 
-INtiuition: tau is non observable if the automaton allows any tau transition from holes, and the global transition resulting from a tau in a hole is a tau transition not changing the action state.
+Intuition: tau is non observable if the automaton allows any tau transition from holes, and the global transition resulting from a tau in a hole is a tau transition not changing the action state.
 \TODO{Id(s) is the identity function on variables of state s}
@@
 \]
-Then there is ag weak  open transition of the following form in $\WT$:
+Then there is a weak  open transition of the following form in $\WT$:
 \[\openrule
@@
 
-Weak bisimulation can be alternatively defined as a strong bisimulation on the weak open automata, however this would still need a specific definition of strong bisimulation for weau open automata.
+Weak bisimulation can be alternatively defined as a strong bisimulation on the weak open automata, however this would still need a specific definition of strong bisimulation for weak open automata.
 \TODO{polish}
+
+--------------------------------------------------------
+
+We will show that $\mathcal{R}''$ is a weak FH-bisimulation. Consider 
+$(s,u|\Pred_{s,u})\in\mathcal{R}''$.
+Then there is a set of states of $\mathcal{S}_3$ relating $s$ and $u$, let $(p)^{p\in \mathcal{S}_2}$ be this family.
+We have $\Pred_{s,u} = \bigvee_{p\in \mathcal{S}_2} \Pred_{s,p}\land\Pred_{p,u}$.
+
+\medskip
+
+For any $p\in \mathcal{S}_2$ by definition of $\mathcal{R}''$, $(s,p|\Pred_{s,p})\in\mathcal{R}$,  and $(p,u|\Pred_{p,u})\in\mathcal{R}'$. 
+We have the following by definition of weak bisimulation:\\
+For any open transition $OT$ in $\mathcal{T}_1$ originating from $s$.
+       	\begin{mathpar}
+       	\openrule
+       	{
+       		\beta_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
+       	{s \OTarrow {\alpha} {s}'}  \qquad (1)   	
+       	\end{mathpar}
+
+       	There exist weak open transitions $OT_{x}^{x\in X} \subseteq \mathcal{T}_2$:
+
+       	\begin{mathpar} 
+       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
+       	\openrule
+       	{
+       		\gamma_{j x}^{j\in J_{x}}, \Pred_{OT_{x}},\Post_{OT_{x}}}
+       	{p \OTWeakarrow {\alpha_{x}} p'_{x}}\qquad (2)
+       	%         \right)
+       	\end{mathpar}
+
+       	such that  $\forall x, J_1=J_{x}, (s',p'_{x}|\Pred\,'_{{x}})\in 
+       	\mathcal{R}$;
+       	and  \\
+
+       	$\Pred_{s,p} \land \Pred_{OT}\\
+       	\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
+       	\left( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_{x}}
+       	\land \alpha\!=\!\alpha_{x} \land
+       	\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\right)$\\
+
+For any open transition $OT_{x}$, since
+       	$(p,u_x|\Pred_{x})\in\mathcal{R}'$ there exist open transitions
+       	$OT_{xy}^{y\in Y} \subseteq \mathcal{T}_3$:
+
+       	\begin{mathpar}  	
+       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
+       	\openrule
+       	{
+       		\gamma_{j  x y}^{j\in J_{xy}}, 
+       		\Pred_{OT_{xy}},\Post_{OT_{xy}}}
+       	{u \OTWeakarrow {\alpha_{xy}} u'_{xy}}\qquad (3)
+       	%         \right)    	
+       	\end{mathpar}
+       	such that  $\forall y, J_{x}=J_{xy}, 
+       	(p'_{x},u'_{xy}|\Pred\,'_{{x,xy}})\in \mathcal{R}'$; and  \\
+       	$\Pred_{p,u} \land \Pred_{OT_{x}}\\
+       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
+       	\left( \forall j. \gamma_{jx}=\gamma_{jxy}  \Rightarrow \Pred_{OT_{xy}}
+       	\land \alpha_{x}\!=\!\alpha_{xy} \land
+       	\Pred\,'_{{x,xy}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}\right)$.\\
+
+This is verified for all $p \in \mathcal{S}_2$. Overall,  we have a family of open 
+       	transitions 
+       	$OT_{xy}^{x\in X, 
+       		y\in Y} \subseteq \mathcal{T}_3$ that should simulate \emph{OT}.
+
+We have  $\forall y, \forall x,  J_1=J_{x}=J_{xy}, 
+       	({s}',u'_{xy}|\Pred\,'_{{xy}})\in \mathcal{R}''$ for some $\Pred\,'_{{xy}}$.  Indeed,  for any $x$ and $y$, we have $p'_{x}$ relates ${s}'$ and $u'_{xy}$, indeed we have
+$(s',p'_{x}|\Pred\,'_{{x}})\in \mathcal{R}$
+       	and $(p'_{x},u'_{xy}|\Pred\,'_{{x,xy}})\in \mathcal{R}'$. For states ensuring the transitivity relation we have   
+       		 for all  $x$, $y$, $\Pred\,'_{x}\land 
+       	\Pred\,'_{{x,xy}}\implies 
+       	\Pred\,'_{{xy}}$.
+
+\TODO{We need to prove that we have the following  relation:}  \\     	
+       	\begin{small}
+ $\Pred_{s,u} \land \Pred_{OT}\\
+       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}
+       		\left( \forall j. \vis{\beta_j}=\gamma_{jxy}  \Rightarrow \Pred_{OT_{xy}}
+       		\land \alpha\!=\!\alpha_{xy} \land
+       		\Pred\,'_{{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{xy}}}\right)$.
+       	\end{small}
+
+\noindent By rule given in (2) we have for all state $p$:\\
+\begin{small}
+$\big(\Pred_{s,p} \land \Pred_{OT}\big)\land\Pred_{p,u}\\
+       		\hspace{1cm} \implies\!\!\! \Big(\bigvee_{x\in X}
+       		\left( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_{x}}
+       		\land \alpha\!=\!\alpha_{x} \land
+       		\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\right)\Big)\land\Pred_{p,u}\\
+       		%
+       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
+       	\Big( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow 
+       		(\Pred_{OT_{x}}\land\Pred_{p,u})
+       		\land \alpha\!=\!\alpha_{x} \land
+       		\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\Big).\\
+       		%
+       		$
+  \end{small}
+
+\noindent By rule given in (3) we get:     \\	
+	\begin{small}
+$    \big(\Pred_{s,p} \land \Pred_{OT}\big)\land\Pred_{p,u}\\
+\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
+       		\bigg( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Big(\bigvee_{y\in Y} 
+       		\big( \forall j'.\gamma_{j'x}=\gamma_{j'xy}  \Rightarrow \Pred_{OT_{xy}}
+       		\land \alpha_{x}\!=\!\alpha_{xy}\land\\
+       		%
+ \Pred\,'_{{x,xy}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}\Big)
+       		\land \alpha\!=\!\alpha_{x} \land
+       \Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\bigg)\\
+       		%
+ \hspace{1cm} \implies\!\!\! \bigvee_{x\in X} \bigvee_{y\in Y}
+       		\bigg(\forall j, j'.\vis{\beta_j}=\gamma_{jx} \land \gamma_{j'x}=\gamma_{j'xy}
+       		\Rightarrow \Big( 
+       		\Pred_{OT_{xy}}
+       		\land \alpha\!=\alpha_{x}\!=\!\alpha_{xy} \land
+       \Pred\,'_{{x,xy}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}
+       		\land
+\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\Big)\bigg).
+       		$
+       \end{small}
+
+\medskip
+\noindent Because of variables domains independence we  have:\\ 
+    $\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\land 
+       	\Pred\,'_{{x,xy}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}
+       	\Leftrightarrow\\ % we changed =
+\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}\land
+       \Pred\,'_{{x,xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}} \Leftrightarrow
+\big(\Pred\,'_{{x}} \land   \Pred\,'_{{x,xy}}\big)   \subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}} \\	\implies\Pred\,'_{{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}
+   \Leftrightarrow  \Pred\,'_{{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{xy}}} $\\
+
+\noindent This allows us to conclude, with $\Pred_{s,u} = \bigvee_{p\in \mathcal{S}_2} 
+       	\Pred_{s,p}\land\Pred_{p,u}$:
+
+      	\begin{small}     	
+$\Pred_{s,u} \land \Pred_{OT}\\
+\hspace{1cm} \implies\!\!\! \bigvee_{p\in \mathcal{S}_2} \big(
+	\Pred_{s,p}\land\Pred_{p,u}\big) \land \Pred_{OT}\\
+\hspace{1cm} \implies\!\!\!\bigvee_{p\in \mathcal{S}_2}\bigg(\!\!
+ \bigvee_{x\in X}\!\!\bigvee_{y\in Y}\!\!
+\Big( \forall j, j'.\vis{\beta_j}=\gamma_{jx} \land \gamma_{j'x}=\gamma_{j'xy}
+\Rightarrow \Big( 
+\Pred_{OT_{xy}}
+\land \alpha\!=\alpha_{x}\!=\!\alpha_{xy}\\~\hspace{3em}~ \land
+\Pred\,'_{{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{xy}}}\Big)\Big)\bigg)
+\\
+\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\!\!\bigvee_{y\in Y}\!\!\bigvee_{p\in \mathcal{S}_2}\!\!
+\Big(\forall j.\vis{\beta_j}\!=\!\gamma_{jxy}  \Rightarrow \Pred_{OT_{xy}}
+\land\, \alpha\!=\!\alpha_{xy} \land
+\Pred\,'_{{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{xy}}}\Big)$.
+  \end{small}
+
+----------------------------------------------
 
@@
 - construction of the predicate\\
-- defn / elimination of the intermediaite variables\\
+- defn / elimination of the intermediate variables\\
 - construction of the weak OT.
@@
 then transmitting the message to the receiver (if the sender and
-receiver control bits are equal), and to the environnement. The two
+receiver control bits are equal), and to the environment. The two
 firts OTs are internal, the last one is visible, so it constitute a

### 2018-06-29 2016-Weak-FH-Bisim/WeakBisim.tex
moved thm
saturation lemma
lemma Weak OT decomposition

@@
 $I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}$.
-\def\WT{\mathcal{WT}}
 \begin{definition}[Weak open transition]\label{def:weakOT}
@@
 
-\TODO{the formal view is not much interesting}
+\TODO{ the formal view is not much interesting}
 
@@
 
+\TODO{From Definition \ref{def:buildweakOT} we can prove following lemma that enables us to conclude FH-weak bisimulation coincides with  FH-bisimulation ... what does coincide mean here?}
+
+\begin{lemma} \TODO{!!! formalisation of the lemma is cumbersome}
+$s (\OTarrow{\tau})\!\!* (\OTarrow{\alpha})(\OTarrow{\tau})\!\!* s'$ iff $s \OTWeakarrow {\alpha} s'$
+\end{lemma}
+
+\begin{proof} ($\Rightarrow$)
+
+\end{proof}
+
 \subsection{Weak FH-bisimulation}
@@
 --------------------------------------------------------
+
+\begin{theorem}[Weak FH-Bisimulation is an equivalence]\label{thm-weak-equiv} Suppose $\mathcal{R}$ 
+is a weak FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
+reflexive, symmetric and transitive.
+\end{theorem}
 
@@
 
-\begin{theorem}[Weak FH-Bisimulation is an equivalence]\label{thm-weak-equiv} Suppose $\mathcal{R}$ 
-is a weak FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
-reflexive, symmetric and transitive.
-\end{theorem}
-
 \subsection{Weak bisimulation for open pNets}
@@
 \end{property}
+
+\begin{definition}[Notation: Semantics of pNets as a weak open automaton]
+Let $A$ be the open automaton expressing the semantics of an open \pNet: $\pNet$; let $<J,\mathcal{S},s_0,  \WT>$ be the weak open automata derived from $A$.
+For any $\WOT\in\WT$, we denote $\pNet \models \WOT$, this defines the semantics of the pNet \pNet as a weak open automaton.
+\end{definition}
+
+\TODO{move text below}
 
@@
 	\]
-		with  $J\cap\Holes(Q)\neq\emptyset$ or $I\cap L_Q\neq 
-		\emptyset$, i.e. $Q$ takes part in the reduction.
+		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.
 		 Then there exist $v_Q$, $\Pred\,'$, $\Pred\,''$, 
@@
 similar.\qed
+
+       \section{Weak FH-bisimulation lemmas and proofs}
+\begin{lemma}[Weak OT decomposition]\label{lem-decompose} 
+	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
+	lemma imply that $Q$ is 
+	not a \pLTS\ but a similar lemma can be proven for a pLTS $Q$}:
+	\[ P[Q]_{j_0}  
+		\models
+		{\openrule
+			{
+				\gamma_j^{j\in J}, \Pred,  
+				\Post}
+			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
+				\ostate{s_i'^{\, i\in L}}}
+		}
+	\]
+		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.
+		 Then there exist $v_Q$, $\Pred\,'$,  
+		$\Post\,'$,   $\gamma_{j_0}=[\beta_0..\beta_n]$, and for all $p\in[0..n]$ there exist $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
+		%\[
+		\begin{mathpar}
+		P\models{\openrule
+			{
+				\gamma_j^{j\in (J_p\setminus \Holes(Q)) \cup \{j_0\}}, 
+				\Pred\,',  
+				\Post\,'}
+			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
+				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
+		}%\]
+	\vspace{-2.2ex}\\\text{and for all $p\in[0..n]$~~}
+		%\[
+		Q\models{\openrule
+			{
+				\gamma_{p j}^{j\in J_p}, \Pred_p,  
+				\Post_p}
+			{\ostate{s_i^{i\in L_Q}} \OTWeakarrow {\alpha_i}
+				\ostate{s_{p i}^{\,i\in L_Q}}}
+		}%\]
+\\
+		\text{and~~}  \bigcup_{\begin{array}{l}
+p\in[0..n]\\{j\in J_p}
+\end{array}} J_{p j} = J\cap\Holes(Q) \qquad
+ \text{and\quad} \forall i \in L_Q.\, s_{n i} = s_i'\\{\hspace{-3ex}}\text{and~~} \Pred \iff \Pred\,'
+		\land \!\!\bigwedge_{p\in[0..n]}(\alpha_p=\beta_p\land \Pred_p) \qquad\text{and~}
+\Post=\Post\,'\uplus\!\! \biguplus_{p\in[0..n]}
+		\Post_p  
+		\end{mathpar}
+where $\Post_p$ only act upon variables of 
+		$\Leaves(Q)$.
+\end{lemma}
 

### 2018-07-02 2016-Weak-FH-Bisim/WeakBisim.tex
new TODOs

@@
 \TODO{should we use iff/implies or LeftRightArrow/Rightarrow}
-
-Ludo
 \begin{itemize}
-\item[x] rewrite Tr2 and open transition with actions
-\item[x] $v'\to \alpha'$ dans pred sv et enlever l exists
-\item[x] $\beta$ ou $b$
-\item[x] propager Tr2 dans l annexe
-\item[x] add simple equivalence on OT -- fait a minima 
-\item[x] explain the 2 level logic
+\item reorga sec weak bisim + thm -> 10 Juil
+\item  intro et orga globale du papier
 \end{itemize}
-=== 18 Avril
+
+%Ludo
+%\begin{itemize}
+%\item[x] rewrite Tr2 and open transition with actions
+%\item[x] $v'\to \alpha'$ dans pred sv et enlever l exists
+%\item[x] $\beta$ ou $b$
+%\item[x] propager Tr2 dans l annexe
+%\item[x] add simple equivalence on OT -- fait a minima 
+%\item[x] explain the 2 level logic
+%\end{itemize}
+%=== 18 Avril
 \medskip
@@
 \begin{itemize}
-\item re-ecrire transitions page 14 comment les presenter?
-\item arbre de deduction
-\item exemple avec actions
+\item nettoyage -> 5 juil
+\item example -> fin aout -> qq transitions dans l abp
+%\item re-ecrire transitions page 14 comment les presenter?
+%\item arbre de deduction
+%\item exemple avec actions
 \end{itemize}
-=== 20 Avril?
+%=== 20 Avril?
 \medskip
@@
 \begin{itemize}
-\item [x] uniformiser p et P pour les pnets 
-\item [x] relectures
+\item preuve transitivite -> 10 juil
+\item proofs of new theorems -> fin aout
+%\item [x] uniformiser p et P pour les pnets 
+%\item [x] relectures
 \end{itemize}

### 2018-07-02 2016-Weak-FH-Bisim/WeakBisim.tex
updated date
Petits nettoyages Eric

--- 2018-06-29 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
-%\TODO{Add somewhere a subsection ``running example'' ?}
-
 It is important to understand the difference between the red dotted rule and a normal 
@@
   \caption{Proof of transition $OT_2$ (with interaction of processes $P$ and $Q$) for 
-  ``P>>(Q>>R)'' \TODO{remove?}}
+  ``P>>(Q>>R)'' \TODO{Change for the new example or remove?}}
   \label{usingrules:OT2}
@@
 
-\TODO{Eric: refine the algorithm description - \ERIC{Done, can you check ?}}
+% \TODO{Eric: refine the algorithm description - \ERIC{Done, can you check ?}}
 
@@
 
-\subsection{Post-processing: Elimination of intermediate variables}
-
-While building the open transitions, many new variable names are
-created, as fresh local variables of synchronisation vectors, and
-fresh result variables of intermediate OTs. While these are required
-for the semantic construction, they are not significant in the
-resulting open automaton. In fact they carry information on the
-internal structure of the pNet system, and this information should
-\_not\_ be visible when looking at the system as a black box, and in
-particular when comparing its behaviour with another system, e.g. by
-bisimulation.
-
-In the resulting predicate the only significant variables are :\\
-- the input variables of pLTS transitions \TODO{heu, non, meme pas, si
-  ce sont des comm internes!}\\
-- the actions of holes\\
-- the result action at toplevel.
-
-So we transform the predicates of the resulting OTs, eliminating all
-intermediate variables. \TODO{Explain why this should work !! Maybe
-  need to be more precise on unification in the matching...}
+%% \subsection{Post-processing: Elimination of intermediate variables}
+
+%% While building the open transitions, many new variable names are
+%% created, as fresh local variables of synchronisation vectors, and
+%% fresh result variables of intermediate OTs. While these are required
+%% for the semantic construction, they are not significant in the
+%% resulting open automaton. In fact they carry information on the
+%% internal structure of the pNet system, and this information should
+%% \_not\_ be visible when looking at the system as a black box, and in
+%% particular when comparing its behaviour with another system, e.g. by
+%% bisimulation.
+
+%% In the resulting predicate the only significant variables are :\\
+%% - the input variables of pLTS transitions \TODO{heu, non, meme pas, si
+%%   ce sont des comm internes!}\\
+%% - the actions of holes\\
+%% - the result action at toplevel.
+
+%% So we transform the predicates of the resulting OTs, eliminating all
+%% intermediate variables. \TODO{Explain why this should work !! Maybe
+%%   need to be more precise on unification in the matching...}
 
@@
 
-\RAB{We let $\gamma$ range over sets of words and use $\dotcup$ as the union that appends sets of words.}
+\RAB{We let $\gamma$ range over words (of action terms) and use $\dotcup$ as the union that appends words.}
 
@@
          {
-           \gamma_j^{j\in J},\symb{True},Id(s)}
+           \gamma_j^{j\in J},\Pred,\Post}
          {s \OTWeakarrow {\alpha} s'}
@@
 
-\TODO{ the formal view is not much interesting}
-
-\begin{property}[Weak open transition transitivity]
-Let $A$ be an open automaton, and $<J,\mathcal{S},s_0,\WT>$ a weak open automaton derived from $A$.
-Suppose we have the following weak open transitions in $\WT$:
-\[\openrule
-         {
-           \overline{\gamma_1},\Pred_1,\Post_1   }
-         {s \OTWeakarrow {\tau} s_1}
-\qquad 
-\openrule
-         {
-           \overline{\gamma_2},\Pred_2,\Post_2   }
-         {s_1 \OTWeakarrow {\alpha} s_2}
-\qquad
-\openrule
-         {
-           \overline{\gamma_3},\Pred_3,\Post_3   }
-         {s_2 \OTWeakarrow {\tau} s_3}
-\]
-Then there is a weak  open transition of the following form in $\WT$:
-\[\openrule
-         {
-           \overline{\gamma},\Pred,\Post   }
-         {s \OTWeakarrow {\alpha} s_3}
-\]
-Suppose additionally $\Post_3=({x_k\gets e_k})^{k\in K}$, we have the following
-\[
-\begin{array}{rcl}
-\gamma&=& \gamma_1\dotcup\gamma_2\dotcup\gamma_3\\
-\Pred&=&\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}\\
-\Post &=& ({x_k\gets ((e_k\subst{\Post_2})\subst{\Post_1})})^{k\in K}
-\end{array}\]
-\end{property}
+%% \TODO{ the formal view is not much interesting}
+
+%% \begin{property}[Weak open transition transitivity]
+%% Let $A$ be an open automaton, and $<J,\mathcal{S},s_0,\WT>$ a weak open automaton derived from $A$.
+%% Suppose we have the following weak open transitions in $\WT$:
+%% \[\openrule
+%%          {
+%%            \overline{\gamma_1},\Pred_1,\Post_1   }
+%%          {s \OTWeakarrow {\tau} s_1}
+%% \qquad 
+%% \openrule
+%%          {
+%%            \overline{\gamma_2},\Pred_2,\Post_2   }
+%%          {s_1 \OTWeakarrow {\alpha} s_2}
+%% \qquad
+%% \openrule
+%%          {
+%%            \overline{\gamma_3},\Pred_3,\Post_3   }
+%%          {s_2 \OTWeakarrow {\tau} s_3}
+%% \]
+%% Then there is a weak  open transition of the following form in $\WT$:
+%% \[\openrule
+%%          {
+%%            \overline{\gamma},\Pred,\Post   }
+%%          {s \OTWeakarrow {\alpha} s_3}
+%% \]
+%% Suppose additionally $\Post_3=({x_k\gets e_k})^{k\in K}$, we have the following
+%% \[
+%% \begin{array}{rcl}
+%% \gamma&=& \gamma_1\dotcup\gamma_2\dotcup\gamma_3\\
+%% \Pred&=&\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}\\
+%% \Post &=& ({x_k\gets ((e_k\subst{\Post_2})\subst{\Post_1})})^{k\in K}
+%% \end{array}\]
+%% \end{property}
 
@@
 \subsection{Weak bisimulation for open pNets}
-\begin{definition}[Non-observability of silent actions]~\\
+\begin{definition}[Non-observability of silent actions for pNets]~\\
 A pNet $\mylangle \pNet_i^{i\in I} , \Sort_j^{j\in J}, \overline{\symb{SV}}\myrangle$
- \emph{cannot observe silent actions} if it verifies:\\ $\forall i\in I\uplus J.\, \SV{(i\mapsto \tau)}{\tau}{\symb{True}}\in \overline{\symb{SV}}$ and $\forall i,j\in I\uplus J.\,i\neq j \Rightarrow \alpha_i\neq\tau$
+ \emph{cannot observe silent actions} if it verifies:\\ $\forall i\in I\uplus J.\, \SV{(i\mapsto \tau)}{\tau}{\symb{True}}\in \overline{\symb{SV}}$ and $\forall SV_k\in \overline{\symb{SV}}, \forall i,j\in I_k\uplus J_k.\,i\neq j \Rightarrow \alpha'_k\neq\tau$
 \end{definition}
@@
 Let $A$ be the open automaton expressing the semantics of an open \pNet: $\pNet$; let $<J,\mathcal{S},s_0,  \WT>$ be the weak open automata derived from $A$.
-For any $\WOT\in\WT$, we denote $\pNet \models \WOT$, this defines the semantics of the pNet \pNet as a weak open automaton.
+For any $\WOT\in\WT$, we denote $\pNet \models \WOT$, this defines the semantics of the pNet $\pNet$ as a weak open automaton.
 \end{definition}
 
-\TODO{move text below}
-
-\begin{property}[Decomposition of weak open transitions] \TODO{TODO}
-Let $A$ be the open automaton that is the semantics of a \pNet $P$, and $<J,\mathcal{S},s_0,\WT>$ a weak open automaton derived from $A$.
-Suppose we have the following weak open transitions in $\WT$:
-\[\openrule
-         {
-           \overline{\gamma_1},\Pred_1,\Post_1   }
-         {s \OTWeakarrow {\tau} s_1}
-\qquad 
-\openrule
-         {
-           \overline{\gamma_2},\Pred_2,\Post_2   }
-         {s_1 \OTWeakarrow {\alpha} s_2}
-\qquad
-\openrule
-         {
-           \overline{\gamma_3},\Pred_3,\Post_3   }
-         {s_2 \OTWeakarrow {\tau} s_3}
-\]
-Then there is ag weak  open transition of the following form in $\WT$:
-\[\openrule
-         {
-           \overline{\gamma},\Pred,\Post   }
-         {s \OTWeakarrow {\alpha} s_3}
-\]
-Suppose additionally $\Post_3=({x_k\gets e_k})^{k\in K}$, we have the following
-\[
-\begin{array}{rcl}
-\gamma&=& \gamma_1\dotcup\gamma_2\dotcup\gamma_3\\
-\Pred&=&\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}\\
-\Post &=& ({x_k\gets ((e_k\subst{\Post_2})\subst{\Post_1})})^{k\in K}
-\end{array}\]
-\end{property}
+%% \TODO{move text below}
+
+%% \begin{property}[Decomposition of weak open transitions] \TODO{TODO}
+%% Let $A$ be the open automaton that is the semantics of a \pNet $P$, and $<J,\mathcal{S},s_0,\WT>$ a weak open automaton derived from $A$.
+%% Suppose we have the following weak open transitions in $\WT$:
+%% \[\openrule
+%%          {
+%%            \overline{\gamma_1},\Pred_1,\Post_1   }
+%%          {s \OTWeakarrow {\tau} s_1}
+%% \qquad 
+%% \openrule
+%%          {
+%%            \overline{\gamma_2},\Pred_2,\Post_2   }
+%%          {s_1 \OTWeakarrow {\alpha} s_2}
+%% \qquad
+%% \openrule
+%%          {
+%%            \overline{\gamma_3},\Pred_3,\Post_3   }
+%%          {s_2 \OTWeakarrow {\tau} s_3}
+%% \]
+%% Then there is ag weak  open transition of the following form in $\WT$:
+%% \[\openrule
+%%          {
+%%            \overline{\gamma},\Pred,\Post   }
+%%          {s \OTWeakarrow {\alpha} s_3}
+%% \]
+%% Suppose additionally $\Post_3=({x_k\gets e_k})^{k\in K}$, we have the following
+%% \[
+%% \begin{array}{rcl}
+%% \gamma&=& \gamma_1\dotcup\gamma_2\dotcup\gamma_3\\
+%% \Pred&=&\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}\\
+%% \Post &=& ({x_k\gets ((e_k\subst{\Post_2})\subst{\Post_1})})^{k\in K}
+%% \end{array}\]
+%% \end{property}
 
@@
 	Consider two weak FH-bisimilar pNets with an arbitrary number of holes, when replacing, 
-	inside those two original pNets, a subset of the holes by FH-bisimilar pNets, we 
+	inside those two original pNets, a subset of the holes by weak FH-bisimilar pNets, we 
 	obtain two weak FH-bisimilar pNets.
@@
 \TODO{Here we should include:
-  \\  - A sufficient condition for an open PNet to preserve Weak-FH,
-  including: 1) no non-deterministic Tau-choice in the pLTSs, 2) a
-  synch vector propagating Tau from a subnet $pNet_i$ mandatory
-  everytime $pNet_i$ can do some visible action in the current
-  context, 3) if we have a vector <Tau, -, a, - > --> b with ``a'' a visible
-  action of some CLOSED subnet, then b=Tau. 
+  %% \\  - A sufficient condition for an open PNet to preserve Weak-FH,
+  %% including: 1) no non-deterministic Tau-choice in the pLTSs, 2) a
+  %% synch vector propagating Tau from a subnet $pNet_i$ mandatory
+  %% everytime $pNet_i$ can do some visible action in the current
+  %% context, 3) if we have a vector <Tau, -, a, - > --> b with ``a'' a visible
+  %% action of some CLOSED subnet, then b=Tau. 
   \\  - the corresponding Congruence theorem

### 2018-07-02 2016-Weak-FH-Bisim/WeakBisim.tex

@@
 \TODO{should we use iff/implies or LeftRightArrow/Rightarrow}
-
-Ludo
 \begin{itemize}
-\item[x] rewrite Tr2 and open transition with actions
-\item[x] $v'\to \alpha'$ dans pred sv et enlever l exists
-\item[x] $\beta$ ou $b$
-\item[x] propager Tr2 dans l annexe
-\item[x] add simple equivalence on OT -- fait a minima 
-\item[x] explain the 2 level logic
+\item reorga sec weak bisim + thm -> 10 Juil
+\item  intro et orga globale du papier -> fin aout
 \end{itemize}
-=== 18 Avril
+
+%Ludo
+%\begin{itemize}
+%\item[x] rewrite Tr2 and open transition with actions
+%\item[x] $v'\to \alpha'$ dans pred sv et enlever l exists
+%\item[x] $\beta$ ou $b$
+%\item[x] propager Tr2 dans l annexe
+%\item[x] add simple equivalence on OT -- fait a minima 
+%\item[x] explain the 2 level logic
+%\end{itemize}
+%=== 18 Avril
 \medskip
@@
 \begin{itemize}
-\item [x] uniformiser p et P pour les pnets 
-\item [x] relectures
+\item preuve transitivite -> 10 juil
+\item proofs of new theorems -> fin juillet
+%\item [x] uniformiser p et P pour les pnets 
+%\item [x] relectures
 \end{itemize}

### 2018-07-03 2016-Weak-FH-Bisim/WeakBisim.tex
orga section weak bisim + theorems + decomp lemmas in appendix

@@
 composability and FH-bisimilarity.
-\begin{corollary}[Composability]
+\begin{theorem}[Composability]
 	Consider two FH-bisimilar pNets with an arbitrary number of holes, when replacing, 
@@
 	obtain two FH-bisimilar pNets.
-\end{corollary}
+\end{theorem}
 %
@@
 %% their comparison.
+
+\subsection{Defining weak open transitions}
 
@@
 
---------------------------------------------------------
-
 \begin{theorem}[Weak FH-Bisimulation is an equivalence]\label{thm-weak-equiv} Suppose $\mathcal{R}$ 
@@
 \end{theorem}
-
-We will show that $\mathcal{R}''$ is a weak FH-bisimulation. Consider 
-$(s,u|\Pred_{s,u})\in\mathcal{R}''$.
-Then there is a set of states of $\mathcal{S}_3$ relating $s$ and $u$, let $(p)^{p\in \mathcal{S}_2}$ be this family.
-We have $\Pred_{s,u} = \bigvee_{p\in \mathcal{S}_2} \Pred_{s,p}\land\Pred_{p,u}$.
-
-\medskip
-
-For any $p\in \mathcal{S}_2$ by definition of $\mathcal{R}''$, $(s,p|\Pred_{s,p})\in\mathcal{R}$,  and $(p,u|\Pred_{p,u})\in\mathcal{R}'$. 
-We have the following by definition of weak bisimulation:\\
-For any open transition $OT$ in $\mathcal{T}_1$ originating from $s$.
-       	\begin{mathpar}
-       	\openrule
-       	{
-       		\beta_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
-       	{s \OTarrow {\alpha} {s}'}  \qquad (1)   	
-       	\end{mathpar}
-
-       	There exist weak open transitions $OT_{x}^{x\in X} \subseteq \mathcal{T}_2$:
-
-       	\begin{mathpar} 
-       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
-       	\openrule
-       	{
-       		\gamma_{j x}^{j\in J_{x}}, \Pred_{OT_{x}},\Post_{OT_{x}}}
-       	{p \OTWeakarrow {\alpha_{x}} p'_{x}}\qquad (2)
-       	%         \right)
-       	\end{mathpar}
-
-       	such that  $\forall x, J_1=J_{x}, (s',p'_{x}|\Pred\,'_{{x}})\in 
-       	\mathcal{R}$;
-       	and  \\
-
-       	$\Pred_{s,p} \land \Pred_{OT}\\
-       	\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-       	\left( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_{x}}
-       	\land \alpha\!=\!\alpha_{x} \land
-       	\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\right)$\\
-
-For any open transition $OT_{x}$, since
-       	$(p,u_x|\Pred_{x})\in\mathcal{R}'$ there exist open transitions
-       	$OT_{xy}^{y\in Y} \subseteq \mathcal{T}_3$:
-
-       	\begin{mathpar}  	
-       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
-       	\openrule
-       	{
-       		\gamma_{j  x y}^{j\in J_{xy}}, 
-       		\Pred_{OT_{xy}},\Post_{OT_{xy}}}
-       	{u \OTWeakarrow {\alpha_{xy}} u'_{xy}}\qquad (3)
-       	%         \right)    	
-       	\end{mathpar}
-       	such that  $\forall y, J_{x}=J_{xy}, 
-       	(p'_{x},u'_{xy}|\Pred\,'_{{x,xy}})\in \mathcal{R}'$; and  \\
-       	$\Pred_{p,u} \land \Pred_{OT_{x}}\\
-       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
-       	\left( \forall j. \gamma_{jx}=\gamma_{jxy}  \Rightarrow \Pred_{OT_{xy}}
-       	\land \alpha_{x}\!=\!\alpha_{xy} \land
-       	\Pred\,'_{{x,xy}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}\right)$.\\
-
-This is verified for all $p \in \mathcal{S}_2$. Overall,  we have a family of open 
-       	transitions 
-       	$OT_{xy}^{x\in X, 
-       		y\in Y} \subseteq \mathcal{T}_3$ that should simulate \emph{OT}.
-
-We have  $\forall y, \forall x,  J_1=J_{x}=J_{xy}, 
-       	({s}',u'_{xy}|\Pred\,'_{{xy}})\in \mathcal{R}''$ for some $\Pred\,'_{{xy}}$.  Indeed,  for any $x$ and $y$, we have $p'_{x}$ relates ${s}'$ and $u'_{xy}$, indeed we have
-$(s',p'_{x}|\Pred\,'_{{x}})\in \mathcal{R}$
-       	and $(p'_{x},u'_{xy}|\Pred\,'_{{x,xy}})\in \mathcal{R}'$. For states ensuring the transitivity relation we have   
-       		 for all  $x$, $y$, $\Pred\,'_{x}\land 
-       	\Pred\,'_{{x,xy}}\implies 
-       	\Pred\,'_{{xy}}$.
-
-\TODO{We need to prove that we have the following  relation:}  \\     	
-       	\begin{small}
- $\Pred_{s,u} \land \Pred_{OT}\\
-       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}
-       		\left( \forall j. \vis{\beta_j}=\gamma_{jxy}  \Rightarrow \Pred_{OT_{xy}}
-       		\land \alpha\!=\!\alpha_{xy} \land
-       		\Pred\,'_{{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{xy}}}\right)$.
-       	\end{small}
-
-\noindent By rule given in (2) we have for all state $p$:\\
-\begin{small}
-$\big(\Pred_{s,p} \land \Pred_{OT}\big)\land\Pred_{p,u}\\
-       		\hspace{1cm} \implies\!\!\! \Big(\bigvee_{x\in X}
-       		\left( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_{x}}
-       		\land \alpha\!=\!\alpha_{x} \land
-       		\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\right)\Big)\land\Pred_{p,u}\\
-       		%
-       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-       	\Big( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow 
-       		(\Pred_{OT_{x}}\land\Pred_{p,u})
-       		\land \alpha\!=\!\alpha_{x} \land
-       		\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\Big).\\
-       		%
-       		$
-  \end{small}
-
-\noindent By rule given in (3) we get:     \\	
-	\begin{small}
-$    \big(\Pred_{s,p} \land \Pred_{OT}\big)\land\Pred_{p,u}\\
-\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-       		\bigg( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Big(\bigvee_{y\in Y} 
-       		\big( \forall j'.\gamma_{j'x}=\gamma_{j'xy}  \Rightarrow \Pred_{OT_{xy}}
-       		\land \alpha_{x}\!=\!\alpha_{xy}\land\\
-       		%
- \Pred\,'_{{x,xy}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}\Big)
-       		\land \alpha\!=\!\alpha_{x} \land
-       \Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\bigg)\\
-       		%
- \hspace{1cm} \implies\!\!\! \bigvee_{x\in X} \bigvee_{y\in Y}
-       		\bigg(\forall j, j'.\vis{\beta_j}=\gamma_{jx} \land \gamma_{j'x}=\gamma_{j'xy}
-       		\Rightarrow \Big( 
-       		\Pred_{OT_{xy}}
-       		\land \alpha\!=\alpha_{x}\!=\!\alpha_{xy} \land
-       \Pred\,'_{{x,xy}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}
-       		\land
-\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\Big)\bigg).
-       		$
-       \end{small}
-
-\medskip
-\noindent Because of variables domains independence we  have:\\ 
-    $\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\land 
-       	\Pred\,'_{{x,xy}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}
-       	\Leftrightarrow\\ % we changed =
-\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}\land
-       \Pred\,'_{{x,xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}} \Leftrightarrow
-\big(\Pred\,'_{{x}} \land   \Pred\,'_{{x,xy}}\big)   \subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}} \\	\implies\Pred\,'_{{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}
-   \Leftrightarrow  \Pred\,'_{{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{xy}}} $\\
-
-\noindent This allows us to conclude, with $\Pred_{s,u} = \bigvee_{p\in \mathcal{S}_2} 
-       	\Pred_{s,p}\land\Pred_{p,u}$:
-
-      	\begin{small}     	
-$\Pred_{s,u} \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \bigvee_{p\in \mathcal{S}_2} \big(
-	\Pred_{s,p}\land\Pred_{p,u}\big) \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\!\bigvee_{p\in \mathcal{S}_2}\bigg(\!\!
- \bigvee_{x\in X}\!\!\bigvee_{y\in Y}\!\!
-\Big( \forall j, j'.\vis{\beta_j}=\gamma_{jx} \land \gamma_{j'x}=\gamma_{j'xy}
-\Rightarrow \Big( 
-\Pred_{OT_{xy}}
-\land \alpha\!=\alpha_{x}\!=\!\alpha_{xy}\\~\hspace{3em}~ \land
-\Pred\,'_{{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{xy}}}\Big)\Big)\bigg)
-\\
-\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\!\!\bigvee_{y\in Y}\!\!\bigvee_{p\in \mathcal{S}_2}\!\!
-\Big(\forall j.\vis{\beta_j}\!=\!\gamma_{jxy}  \Rightarrow \Pred_{OT_{xy}}
-\land\, \alpha\!=\!\alpha_{xy} \land
-\Pred\,'_{{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{xy}}}\Big)$.
-  \end{small}
+proof in appendix
 
@@
 \end{property}
+
+\TODO{question : we could merge prop 1 and def above, is it better?}
 
@@
 
-\TODO{We will discuss this corollary and the title.}
-\begin{corollary}[Weak Composability]
+\begin{theorem}[Congruence for  weak bisimulation]\label{weak-thm-congr-eq}
+	Consider an open pNet:
+	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
+	\overline{\symb{SV}}\myrangle$.
+	Let $j_0\in J$ be a hole. Let $Q$ and $Q'$ be two weak FH-bisimilar pNets such that 
+	$\Sortop(Q)=\Sortop(Q')=\Sort_{j_0}$\footnote{Note that $\Sortop(Q)=\Sortop(Q')$ is 
+	ensured by 
+	strong bisimilarity.}. Then 
+	$\pNet[Q]_{j_0}$ and 
+	$\pNet[Q']_{j_0}$ are weak FH-bisimilar.
+\end{theorem}
+
+\begin{theorem}[Context equivalencefor  weak bisimulation]\label{weak-thm-ctxt-eq}
+	Consider two weak FH-bisimilar open pNets:
+	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
+	\overline{\symb{SV}}\myrangle$ and 	$\pNet' = \mylangle {\pNet'}_i^{i\in I}, 
+	\Sort_j^{j\in 
+	J}, 	\overline{\symb{SV'}}\myrangle$ 
+	(recall they must have the same holes to be bisimilar).
+	Let $j_0\in J$ be a hole, and $Q$ be a pNet such that $\Sortop(Q)=\Sort_{j_0}$. Then 
+	$\pNet[Q]_{j_0}$ and 
+	$\pNet'[Q]_{j_0}$ are weak FH-bisimilar.
+\end{theorem}
+
+Finally, the previous theorems can be composed to state a general theorem about 
+composability and weak FH-bisimilarity.
+
+\begin{theorem}[Composability of weak bisimulation]\label{weak-compos}
 	Consider two weak FH-bisimilar pNets with an arbitrary number of holes, when replacing, 
@@
 	obtain two weak FH-bisimilar pNets.
-\end{corollary}
+\end{theorem}
 
@@
        \section{Weak FH-bisimulation lemmas and proofs}
+
+\subsection{Weak bisimulation is an equivalence}
+\TODO{moved from body}
+
+\begin{theorem}[Weak FH-Bisimulation is an equivalence]\label{thm-weak-equiv} Suppose $\mathcal{R}$ 
+is a weak FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
+reflexive, symmetric and transitive.
+\end{theorem}
+
+We will show that $\mathcal{R}''$ is a weak FH-bisimulation. Consider 
+$(s,u|\Pred_{s,u})\in\mathcal{R}''$.
+Then there is a set of states of $\mathcal{S}_3$ relating $s$ and $u$, let $(p)^{p\in \mathcal{S}_2}$ be this family.
+We have $\Pred_{s,u} = \bigvee_{p\in \mathcal{S}_2} \Pred_{s,p}\land\Pred_{p,u}$.
+
+\medskip
+
+For any $p\in \mathcal{S}_2$ by definition of $\mathcal{R}''$, $(s,p|\Pred_{s,p})\in\mathcal{R}$,  and $(p,u|\Pred_{p,u})\in\mathcal{R}'$. 
+We have the following by definition of weak bisimulation:\\
+For any open transition $OT$ in $\mathcal{T}_1$ originating from $s$.
+       	\begin{mathpar}
+       	\openrule
+       	{
+       		\beta_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
+       	{s \OTarrow {\alpha} {s}'}  \qquad (1)   	
+       	\end{mathpar}
+
+       	There exist weak open transitions $OT_{x}^{x\in X} \subseteq \mathcal{T}_2$:
+
+       	\begin{mathpar} 
+       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
+       	\openrule
+       	{
+       		\gamma_{j x}^{j\in J_{x}}, \Pred_{OT_{x}},\Post_{OT_{x}}}
+       	{p \OTWeakarrow {\alpha_{x}} p'_{x}}\qquad (2)
+       	%         \right)
+       	\end{mathpar}
+
+       	such that  $\forall x, J_1=J_{x}, (s',p'_{x}|\Pred\,'_{{x}})\in 
+       	\mathcal{R}$;
+       	and  \\
+
+       	$\Pred_{s,p} \land \Pred_{OT}\\
+       	\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
+       	\left( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_{x}}
+       	\land \alpha\!=\!\alpha_{x} \land
+       	\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\right)$\\
+
+For any open transition $OT_{x}$, since
+       	$(p,u_x|\Pred_{x})\in\mathcal{R}'$ there exist open transitions
+       	$OT_{xy}^{y\in Y} \subseteq \mathcal{T}_3$:
+
+       	\begin{mathpar}  	
+       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
+       	\openrule
+       	{
+       		\gamma_{j  x y}^{j\in J_{xy}}, 
+       		\Pred_{OT_{xy}},\Post_{OT_{xy}}}
+       	{u \OTWeakarrow {\alpha_{xy}} u'_{xy}}\qquad (3)
+       	%         \right)    	
+       	\end{mathpar}
+       	such that  $\forall y, J_{x}=J_{xy}, 
+       	(p'_{x},u'_{xy}|\Pred\,'_{{x,xy}})\in \mathcal{R}'$; and  \\
+       	$\Pred_{p,u} \land \Pred_{OT_{x}}\\
+       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
+       	\left( \forall j. \gamma_{jx}=\gamma_{jxy}  \Rightarrow \Pred_{OT_{xy}}
+       	\land \alpha_{x}\!=\!\alpha_{xy} \land
+       	\Pred\,'_{{x,xy}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}\right)$.\\
+
+This is verified for all $p \in \mathcal{S}_2$. Overall,  we have a family of open 
+       	transitions 
+       	$OT_{xy}^{x\in X, 
+       		y\in Y} \subseteq \mathcal{T}_3$ that should simulate \emph{OT}.
+
+We have  $\forall y, \forall x,  J_1=J_{x}=J_{xy}, 
+       	({s}',u'_{xy}|\Pred\,'_{{xy}})\in \mathcal{R}''$ for some $\Pred\,'_{{xy}}$.  Indeed,  for any $x$ and $y$, we have $p'_{x}$ relates ${s}'$ and $u'_{xy}$, indeed we have
+$(s',p'_{x}|\Pred\,'_{{x}})\in \mathcal{R}$
+       	and $(p'_{x},u'_{xy}|\Pred\,'_{{x,xy}})\in \mathcal{R}'$. For states ensuring the transitivity relation we have   
+       		 for all  $x$, $y$, $\Pred\,'_{x}\land 
+       	\Pred\,'_{{x,xy}}\implies 
+       	\Pred\,'_{{xy}}$.
+
+\TODO{We need to prove that we have the following  relation:}  \\     	
+       	\begin{small}
+ $\Pred_{s,u} \land \Pred_{OT}\\
+       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}
+       		\left( \forall j. \vis{\beta_j}=\gamma_{jxy}  \Rightarrow \Pred_{OT_{xy}}
+       		\land \alpha\!=\!\alpha_{xy} \land
+       		\Pred\,'_{{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{xy}}}\right)$.
+       	\end{small}
+
+\noindent By rule given in (2) we have for all state $p$:\\
+\begin{small}
+$\big(\Pred_{s,p} \land \Pred_{OT}\big)\land\Pred_{p,u}\\
+       		\hspace{1cm} \implies\!\!\! \Big(\bigvee_{x\in X}
+       		\left( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_{x}}
+       		\land \alpha\!=\!\alpha_{x} \land
+       		\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\right)\Big)\land\Pred_{p,u}\\
+       		%
+       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
+       	\Big( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow 
+       		(\Pred_{OT_{x}}\land\Pred_{p,u})
+       		\land \alpha\!=\!\alpha_{x} \land
+       		\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\Big).\\
+       		%
+       		$
+  \end{small}
+
+\noindent By rule given in (3) we get:     \\	
+	\begin{small}
+$    \big(\Pred_{s,p} \land \Pred_{OT}\big)\land\Pred_{p,u}\\
+\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
+       		\bigg( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Big(\bigvee_{y\in Y} 
+       		\big( \forall j'.\gamma_{j'x}=\gamma_{j'xy}  \Rightarrow \Pred_{OT_{xy}}
+       		\land \alpha_{x}\!=\!\alpha_{xy}\land\\
+       		%
+ \Pred\,'_{{x,xy}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}\Big)
+       		\land \alpha\!=\!\alpha_{x} \land
+       \Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\bigg)\\
+       		%
+ \hspace{1cm} \implies\!\!\! \bigvee_{x\in X} \bigvee_{y\in Y}
+       		\bigg(\forall j, j'.\vis{\beta_j}=\gamma_{jx} \land \gamma_{j'x}=\gamma_{j'xy}
+       		\Rightarrow \Big( 
+       		\Pred_{OT_{xy}}
+       		\land \alpha\!=\alpha_{x}\!=\!\alpha_{xy} \land
+       \Pred\,'_{{x,xy}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}
+       		\land
+\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\Big)\bigg).
+       		$
+       \end{small}
+
+\medskip
+\noindent Because of variables domains independence we  have:\\ 
+    $\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\land 
+       	\Pred\,'_{{x,xy}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}
+       	\Leftrightarrow\\ % we changed =
+\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}\land
+       \Pred\,'_{{x,xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}} \Leftrightarrow
+\big(\Pred\,'_{{x}} \land   \Pred\,'_{{x,xy}}\big)   \subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}} \\	\implies\Pred\,'_{{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}
+   \Leftrightarrow  \Pred\,'_{{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{xy}}} $\\
+
+\noindent This allows us to conclude, with $\Pred_{s,u} = \bigvee_{p\in \mathcal{S}_2} 
+       	\Pred_{s,p}\land\Pred_{p,u}$:
+
+      	\begin{small}     	
+$\Pred_{s,u} \land \Pred_{OT}\\
+\hspace{1cm} \implies\!\!\! \bigvee_{p\in \mathcal{S}_2} \big(
+	\Pred_{s,p}\land\Pred_{p,u}\big) \land \Pred_{OT}\\
+\hspace{1cm} \implies\!\!\!\bigvee_{p\in \mathcal{S}_2}\bigg(\!\!
+ \bigvee_{x\in X}\!\!\bigvee_{y\in Y}\!\!
+\Big( \forall j, j'.\vis{\beta_j}=\gamma_{jx} \land \gamma_{j'x}=\gamma_{j'xy}
+\Rightarrow \Big( 
+\Pred_{OT_{xy}}
+\land \alpha\!=\alpha_{x}\!=\!\alpha_{xy}\\~\hspace{3em}~ \land
+\Pred\,'_{{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{xy}}}\Big)\Big)\bigg)
+\\
+\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\!\!\bigvee_{y\in Y}\!\!\bigvee_{p\in \mathcal{S}_2}\!\!
+\Big(\forall j.\vis{\beta_j}\!=\!\gamma_{jxy}  \Rightarrow \Pred_{OT_{xy}}
+\land\, \alpha\!=\!\alpha_{xy} \land
+\Pred\,'_{{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{xy}}}\Big)$.
+  \end{small}
+
+\subsection{composition properties}
+\TODO{Ludo: in the next 2 theorems I have a doubt about the biguplus of post p : not sure they should be disjoint, but else we need to do a complex composition  of posts}
 \begin{lemma}[Weak OT decomposition]\label{lem-decompose} 
@@
 		 Then there exist $v_Q$, $\Pred\,'$,  
-		$\Post\,'$,   $\gamma_{j_0}=[\beta_0..\beta_n]$, and for all $p\in[0..n]$ there exist $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
+		$\Post\,'$,   $\gamma_{j_0}=[\beta_0..\beta_n]$, and for all $p\in[0..n]$ there exist $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$.
+s.t.:\\[-2ex]
 		%\[
@@
 				\Post_p}
-			{\ostate{s_i^{i\in L_Q}} \OTWeakarrow {\alpha_i}
-				\ostate{s_{p i}^{\,i\in L_Q}}}
+			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
+				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
 		}%\]
@@
 		\text{and~~}  \bigcup_{\begin{array}{l}
-p\in[0..n]\\{j\in J_p}
-\end{array}} J_{p j} = J\cap\Holes(Q) \qquad
- \text{and\quad} \forall i \in L_Q.\, s_{n i} = s_i'\\{\hspace{-3ex}}\text{and~~} \Pred \iff \Pred\,'
+p\in[0..n]
+\end{array}} J_{p} = J\cap\Holes(Q) \qquad
+ \text{and\qquad} \forall j\in J_p,\,\gamma_j= \mathop{\dot{\bigcup}}_{p\in [0..n]} \gamma_{p j} \\
+ \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred \iff \Pred\,'
 		\land \!\!\bigwedge_{p\in[0..n]}(\alpha_p=\beta_p\land \Pred_p) \qquad\text{and~}
@@
 \end{lemma}
+\TODO{proof}
+
+\begin{lemma}[Weak open transition composition]\label{lem-compose} 
+	Suppose $j_0\in J$ and $\gamma_{j_0}=[\beta_0..\beta_n]$ and additionally:\\[-2ex]
+\begin{mathpar}
+%\[
+P\models{\openrule
+	{
+		\gamma_j^{j\in J}, 
+		\Pred,  
+		\Post}
+	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
+		\ostate{s_i'^{\, i\in L}}}
+}\\
+\text{~~and for all $p\in[0..n]$~~}
+Q\models{\openrule
+	{
+		\gamma_{p j}^{j\in J_p},
+		 \Pred_p,  
+		\Post_p}
+	{\ostate{s_{p i}^{i\in L_p}} \OTWeakarrow {\alpha_p}
+		\ostate{s_{(p+1) i}^{\, i\in L_Q}}}
+}%\]
+\end{mathpar}
+Let 
+\begin{mathpar}
+J_Q=\bigcup_{\begin{array}{l}
+p\in[0..n]
+\end{array}} J_{p}
+\text{\qquad and\qquad} 
+\Pred\,'=\Pred\land   \!\!\bigwedge_{p\in[0..n]}(\alpha_p=\beta_p\land \Pred_p)
+\\
+\forall j\in J_p,\,\gamma_j= \mathop{\dot{\bigcup}}_{p\in [0..n]} \gamma_{p j}
+\end{mathpar}
+Then, we have\\[-2ex]
+	\[ P[Q]_{j_0}  
+	\models
+	{\openrule
+		{
+			\gamma_j^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
+			\Pred\,',  
+			\Post\uplus\biguplus_{p\in[0..n]}
+		\Post_p  }
+		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
+			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
+	}
+	\]
+\end{lemma}
+\TODO{proof}
+
+\TODO{prove the 3 theorems for composability of weak bisim or explain why the proof is similar to strong (thanks to the previous lemmas)}
 

### 2018-07-06 2016-Weak-FH-Bisim/WeakBisim.tex
small changes in open transition holes (set)

@@
          {
-           \gamma_j^{j\in J},\Pred,\Post}
+           \gamma_j^{j\in J'},\Pred,\Post}
          {s \OTWeakarrow {\alpha} s'}
  \end{mathpar}
-	Where $s, s'\in\mathcal{S}$ and $\gamma_j$
+	Where $J'\subseteq J$, $s, s'\in\mathcal{S}$ and $\gamma_j$
         is a list of transitions of the hole $j$, with each element of the list in $\Sort_j$. $\alpha$ is an action 
@@
 \end{mathpar}
- such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
+ such that  $\forall x, \{j\in J_1|\beta_j\neq\tau\}=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
  and  \\
@@
 \hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-   \left( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
+   \left( \forall j\in J_x. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
      \land \alpha\!=\!\alpha_x \land  

### 2018-07-09 2016-Weak-FH-Bisim/WeakBisim.tex
2eme essai
rewriting of proof Theorem 7

@@
 	\openrule
-	{	\beta_j^{j\in J}, \Pred, \Post}
+	{	\beta_j^{j\in J'}, \Pred, \Post}
 	{s \OTarrow {\alpha}s'}
 	\end{mathpar}
-	Where $s, s'\in\mathcal{S}$ and $\beta_j$
+	Where $J'\subseteq$, $s, s'\in\mathcal{S}$ and $\beta_j$
         is a transition of the hole $j$, with $\beta_j\in\Sort_j$. $\alpha$ is an action 
@@
 
-We define $\vis{\overline\beta}$ as the mapping $\overline\beta$  without  invisible actions but where each element is now a list (if length 1).\\ $\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}$ s.t.
-$I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}$.
 \begin{definition}[Weak open transition]\label{def:weakOT}
@@
 \end{definition}
+
+We define $\vis{\overline\beta}$ as the mapping $\overline\beta$  without  invisible actions but where each element is now a list (if length 1).\\ $\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}$ s.t.
+$I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}$.
 
@@
 
-We will show that $\mathcal{R}''$ is a weak FH-bisimulation. Consider 
-$(s,u|\Pred_{s,u})\in\mathcal{R}''$.
-Then there is a set of states of $\mathcal{S}_3$ relating $s$ and $u$, let $(p)^{p\in \mathcal{S}_2}$ be this family.
-We have $\Pred_{s,u} = \bigvee_{p\in \mathcal{S}_2} \Pred_{s,p}\land\Pred_{p,u}$.
+---------------------------------------------------------------------
+
+Consider 3 open automata 
+       	$\mathcal{T}_1$, $\mathcal{T}_2$, $\mathcal{T}_3$ and states $s$, $t$, $u$ 
+       	in those 
+       	automata\footnote{We omit the constraints stating that each $s_x,\,t_x,\,u_x$ is 
+       	in the 
+       	states of 
+       		$\mathcal{T}_1,\,\mathcal{T}_2,\,\mathcal{T}_3$ for the sake of readability}.
+       	Suppose we have $\mathcal{R}$ an FH-bisimulation relation between states of 
+       	$\mathcal{T}_1$ and of  $\mathcal{T}_2$; members of $\mathcal{R}$ are of the form 
+       	$(s,t|\Pred_{s,t})$.
+       	Suppose we also  have $\mathcal{R}'$ an FH-bisimulation relation between states 
+       	of 
+       	$\mathcal{T}_2$ and of  $\mathcal{T}_3$; members of $\mathcal{R}'$ are of the 
+       	form 
+       	$(t,u|\Pred_{t,u})$.
+
+       	Let $\mathcal{R}''$ be the relation: 
+       	\[\mathcal{R}'' = 
+       	\{(s,u|\Pred_{s,u})\,\,\Big|\,\Pred_{s,u}=\bigvee_{\begin{array}{c}       		
+       		(s,t|\Pred_{s,t})\in\mathcal{R}\\ (t,u|\Pred_{t,u})\in\mathcal{R}' 	
+       		\end{array}
+       	}\,\Pred_{s,t}\land\Pred_{t,u}\}\]
+
+This relation is the adaptation of the transitivity to the conditional relationship that 
+defines a bisimulation. Indeed the global disjunction together with the conjunction of 
+predicates plays exactly the role of the intermediate element in a transitivity rule: 
+``there exists an intermediate state'' corresponds to the global disjunction, and the 
+conjunction of states expresses the intermediate predicate is used to ensure 
+satisfiability of the predicate relating the first state to the last one.
+
+       	The relation is built as follows: for each pair of states $s$, $u$, for each 
+       	state 
+       	$t$ such that $\mathcal{R}$ relates $s$ and $t$, and $\mathcal{R}'$ relates 
+       	$t$ 
+       	and $u$, we take the conjunction of the two predicates. The predicates for 
+       	different 
+       	values of $t$ are collected by a disjunction.
+
+       	We will show
+       	that $\mathcal{R}''$ is an FH-bisimulation. Consider 
+       	$(s,u|\Pred_{s,u})\in\mathcal{R}''$. Then there is a set of states of 
+       	$\mathcal{T}_2$ relating $s$ and $u$, let $(t_p)^{p\in P}$ be this family.  
+       	       	We have $\Pred_{s,u} = \bigvee_{p\in P} \Pred_{s,p}\land\Pred_{p,u}$.
 
@@
 
+       	For any $p\in P$ by definition of $\mathcal{R}''$,
+       	$(s,t_p|\Pred_{s,p})\in\mathcal{R}$,  and 
+       	$(t_p,u|\Pred\,'_{p,u})\in\mathcal{R}'$. 
+       	We have 
+       	the 
+       	following by definition of bisimulation:
 For any $p\in \mathcal{S}_2$ by definition of $\mathcal{R}''$, $(s,p|\Pred_{s,p})\in\mathcal{R}$,  and $(p,u|\Pred_{p,u})\in\mathcal{R}'$. 
@@
 
-       	There exist weak open transitions $OT_{x}^{x\in X} \subseteq \mathcal{T}_2$:
+       	There exist weak open transitions $OT_{px}^{x\in X} \subseteq \mathcal{T}_2$:
 
@@
        	{
-       		\gamma_{j x}^{j\in J_{x}}, \Pred_{OT_{x}},\Post_{OT_{x}}}
-       	{p \OTWeakarrow {\alpha_{x}} p'_{x}}\qquad (2)
+       		\gamma_{jpx}^{j\in J_{px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
+       	{t \OTWeakarrow {\alpha_{px}} t_{px}}\qquad (2)
        	%         \right)
@@
 
-       	such that  $\forall x, J_1=J_{x}, (s',p'_{x}|\Pred\,'_{{x}})\in 
+       	such that  $\forall x, \{j\in J_1|\beta_j \neq \tau\}=J_{x}, (s',t_{px}|\Pred\,_{s'\!,{px}})\in 
        	\mathcal{R}$;
@@
        	\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-       	\left( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_{x}}
-       	\land \alpha\!=\!\alpha_{x} \land
-       	\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\right)$\\
-
-For any open transition $OT_{x}$, since
-       	$(p,u_x|\Pred_{x})\in\mathcal{R}'$ there exist open transitions
-       	$OT_{xy}^{y\in Y} \subseteq \mathcal{T}_3$:
+       	\left( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_{px}}
+       	\land \alpha\!=\!\alpha_{px} \land
+       	\Pred\,_{s'\!,{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)$\\
+
+For any open transition $OT_{px}$, since
+       	$(t_p,u|\Pred_{p,u})\in\mathcal{R}'$ there exist open transitions
+       	$OT_{pxy}^{y\in Y} \subseteq \mathcal{T}_3$:
 
@@
        	{
-       		\gamma_{j  x y}^{j\in J_{xy}}, 
-       		\Pred_{OT_{xy}},\Post_{OT_{xy}}}
-       	{u \OTWeakarrow {\alpha_{xy}} u'_{xy}}\qquad (3)
+       		\gamma_{jpxy}^{j\in J_{pxy}}, 
+       		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
+       	{u \OTWeakarrow {\alpha_{pxy}} u_{pxy}}\qquad (3)
        	%         \right)    	
        	\end{mathpar}
-       	such that  $\forall y, J_{x}=J_{xy}, 
-       	(p'_{x},u'_{xy}|\Pred\,'_{{x,xy}})\in \mathcal{R}'$; and  \\
-       	$\Pred_{p,u} \land \Pred_{OT_{x}}\\
+       	such that  $\forall y, J_{px}=J_{pxy}, 
+       	(t_{px},u_{pxy}|\Pred_{{px,pxy}})\in \mathcal{R}'$; and  \\
+       	$\Pred_{p,u} \land \Pred_{OT_{px}}\\
        	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
-       	\left( \forall j. \gamma_{jx}=\gamma_{jxy}  \Rightarrow \Pred_{OT_{xy}}
-       	\land \alpha_{x}\!=\!\alpha_{xy} \land
-       	\Pred\,'_{{x,xy}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}\right)$.\\
-
-This is verified for all $p \in \mathcal{S}_2$. Overall,  we have a family of open 
+       	\left( \forall j. \gamma_{jpx}=\gamma_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
+       	\land \alpha_{px}\!=\!\alpha_{pxy} \land
+       	\Pred_{{px,pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.\\
+
+This is verified for all $p \in P$. Overall,  we have a family of open 
        	transitions 
-       	$OT_{xy}^{x\in X, 
+       	$OT_{xy}^{p\in P, x\in X, 
        		y\in Y} \subseteq \mathcal{T}_3$ that should simulate \emph{OT}.
 
-We have  $\forall y, \forall x,  J_1=J_{x}=J_{xy}, 
-       	({s}',u'_{xy}|\Pred\,'_{{xy}})\in \mathcal{R}''$ for some $\Pred\,'_{{xy}}$.  Indeed,  for any $x$ and $y$, we have $p'_{x}$ relates ${s}'$ and $u'_{xy}$, indeed we have
-$(s',p'_{x}|\Pred\,'_{{x}})\in \mathcal{R}$
-       	and $(p'_{x},u'_{xy}|\Pred\,'_{{x,xy}})\in \mathcal{R}'$. For states ensuring the transitivity relation we have   
-       		 for all  $x$, $y$, $\Pred\,'_{x}\land 
-       	\Pred\,'_{{x,xy}}\implies 
-       	\Pred\,'_{{xy}}$.
+------------------------------------------------------------------
+
+We have  $\forall y, \forall x, \forall p \in P,  \{j \in J_1|\,\beta_j\neq \tau\} =J_{px}=J_{pxy}, 
+       	({s}',u_{pxy}|\Pred_{s',{pxy}})\in \mathcal{R}''$ for some $\Pred_{{s',pxy}}$.  Indeed,  for any $p$, $x$ and $y$,  we have
+$(s',t_{px}|\Pred_{{s'\!,px}})\in \mathcal{R}$
+       	and $(t_{px},u_{pxy}|\Pred_{{px,pxy}})\in \mathcal{R}'$. For states ensuring the transitivity relation we have   
+       		 for all $p$, $x$, $y$, $\Pred_{px}\land 
+       	\Pred_{{px,pxy}}\implies 
+       	\Pred_{{s'\!,pxy}}$.
 
@@
  $\Pred_{s,u} \land \Pred_{OT}\\
-       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}
-       		\left( \forall j. \vis{\beta_j}=\gamma_{jxy}  \Rightarrow \Pred_{OT_{xy}}
-       		\land \alpha\!=\!\alpha_{xy} \land
-       		\Pred\,'_{{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{xy}}}\right)$.
+       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\!\!\bigvee_{y\in Y}\!\!\bigvee_{p\in P}
+       		\left( \forall j. \vis{\beta_j}=\gamma_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
+       		\land \alpha\!=\!\alpha_{pxy} \land
+       		\Pred_{{s',\!xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
        	\end{small}
 
-\noindent By rule given in (2) we have for all state $p$:\\
+\noindent By rule given in (2) we have for all $p$:\\
 \begin{small}
@@
        		\hspace{1cm} \implies\!\!\! \Big(\bigvee_{x\in X}
-       		\left( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_{x}}
-       		\land \alpha\!=\!\alpha_{x} \land
-       		\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\right)\Big)\land\Pred_{p,u}\\
-       		%
-       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-       	\Big( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow 
-       		(\Pred_{OT_{x}}\land\Pred_{p,u})
-       		\land \alpha\!=\!\alpha_{x} \land
-       		\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\Big).\\
+       		\left( \forall j. \vis{\beta_j}=\gamma_{jpx}  \Rightarrow \Pred_{OT_{px}}
+       		\land \alpha\!=\!\alpha_{px} \land
+       		\Pred_{{s'\!,px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\Big)\land\Pred_{p,u}\\
+       		%
+       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\!
+       	\Big( \forall j.\vis{\beta_j}\!=\!\gamma_{jpx}  \Rightarrow 
+       		(\Pred_{OT_{px}}\land\Pred_{p,u})
+       		\land \alpha\!=\!\alpha_{px} \land
+       		\Pred_{{s'\!,px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\Big).\\
        		%
@@
 
-\noindent By rule given in (3) we get:     \\	
+\noindent By rule given in (3) we have:   \\
+$\Pred_{p,u} \land \Pred_{OT_{px}}\\
+       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
+       	\left( \forall j. \gamma_{jpx}=\gamma_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
+       	\land \alpha_{px}\!=\!\alpha_{pxy} \land
+       	\Pred_{{px,pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.\\
+
+\noindent So can rewrite the formula as:\\	
 \begin{small}
@@
 \hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-       		\bigg( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Big(\bigvee_{y\in Y} 
-       		\big( \forall j'.\gamma_{j'x}=\gamma_{j'xy}  \Rightarrow \Pred_{OT_{xy}}
-       		\land \alpha_{x}\!=\!\alpha_{xy}\land\\
-       		%
- \Pred\,'_{{x,xy}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}\Big)
-       		\land \alpha\!=\!\alpha_{x} \land
-       \Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\bigg)\\
-       		%
- \hspace{1cm} \implies\!\!\! \bigvee_{x\in X} \bigvee_{y\in Y}
-       		\bigg(\forall j, j'.\vis{\beta_j}=\gamma_{jx} \land \gamma_{j'x}=\gamma_{j'xy}
-       		\Rightarrow \Big( 
-       		\Pred_{OT_{xy}}
-       		\land \alpha\!=\alpha_{x}\!=\!\alpha_{xy} \land
-       \Pred\,'_{{x,xy}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}
+       	\bigg( \forall j.\vis{\beta_j}\!=\!\gamma_{jpx}  \Rightarrow\\~~\hspace{2em}
+       		\Big(\!\bigvee_{y\in Y}
+       			\left( \forall j'. \gamma_{j'px}\!=\!\gamma_{j'pxy}  \Rightarrow \Pred_{OT_{pxy}}\!\land \alpha_{px}\!=\!\alpha_{pxy}
+\land \Pred_{{px,pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)   \Big)\\~~ \hspace{2em} \land \alpha\!=\!\alpha_{px} \land
+       		\Pred_{{s'\!,px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\bigg).\\
+\hspace{1cm}\implies\!\!\!\!\bigvee_{x\in X} \bigvee_{y\in Y}\bigg(\forall j, j'.\vis{\beta_j}\!=\!\gamma_{jpx}\!\land\!\gamma_{j'px}\!=\!\gamma_{j'pxy}
+ \Rightarrow\\~~\hspace{2em} \Big(\Pred_{OT_{pxy}}\!\land\alpha\!=\alpha_{px}\!=\!\alpha_{pxy} \land 
+       \Pred_{{px,pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}
        		\land
-\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\Big)\bigg).
+\Pred_{{s'\!,px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\Big)\bigg).
        		$
@@
 \noindent Because of variables domains independence we  have:\\ 
-    $\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\land 
-       	\Pred\,'_{{x,xy}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}
+    $\Pred_{{s'\!,px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\land 
+       	\Pred_{{px,pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}
        	\Leftrightarrow\\ % we changed =
-\Pred\,'_{{x}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}\land
-       \Pred\,'_{{x,xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}} \Leftrightarrow
-\big(\Pred\,'_{{x}} \land   \Pred\,'_{{x,xy}}\big)   \subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}} \\	\implies\Pred\,'_{{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{x}}}\subst{\Post_{OT_{xy}}}
-   \Leftrightarrow  \Pred\,'_{{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{xy}}} $\\
-
-\noindent This allows us to conclude, with $\Pred_{s,u} = \bigvee_{p\in \mathcal{S}_2} 
+\Pred_{{s'\!,px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land
+       \Pred_{{px,pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}} \Leftrightarrow
+\big(\Pred_{{s'\!,px}} \land   \Pred_{{px,pxy}}\big)   \subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}} \\	\implies\Pred_{{s'\!,pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}
+\subst{\Post_{OT_{pxy}}}\Leftrightarrow  \Pred_{{s'\!,pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}} $\\
+
+\noindent This allows us to conclude with $\Pred_{s,u} = \bigvee_{p\in P} 
        	\Pred_{s,p}\land\Pred_{p,u}$:
@@
 $\Pred_{s,u} \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \bigvee_{p\in \mathcal{S}_2} \big(
+\hspace{1cm} \implies\!\!\! \bigvee_{p\in P} \big(
 	\Pred_{s,p}\land\Pred_{p,u}\big) \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\!\bigvee_{p\in \mathcal{S}_2}\bigg(\!\!
+\hspace{1cm} \implies\!\!\!\bigvee_{p\in P}\bigg(\!\!
  \bigvee_{x\in X}\!\!\bigvee_{y\in Y}\!\!
-\Big( \forall j, j'.\vis{\beta_j}=\gamma_{jx} \land \gamma_{j'x}=\gamma_{j'xy}
-\Rightarrow \Big( 
-\Pred_{OT_{xy}}
-\land \alpha\!=\alpha_{x}\!=\!\alpha_{xy}\\~\hspace{3em}~ \land
-\Pred\,'_{{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{xy}}}\Big)\Big)\bigg)
+\Big( \forall j, j'.\vis{\beta_j}\!=\!\gamma_{jpx} \land \gamma_{j'px}\!=\!\gamma_{j'pxy}\Rightarrow\\~~\hspace{2em}
+\Big( 
+\Pred_{OT_{pxy}}
+\land \alpha\!=\alpha_{px}\!=\!\alpha_{pxy} \land
+\Pred_{{s'\!,pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\Big)\Big)\bigg)
 \\
-\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\!\!\bigvee_{y\in Y}\!\!\bigvee_{p\in \mathcal{S}_2}\!\!
-\Big(\forall j.\vis{\beta_j}\!=\!\gamma_{jxy}  \Rightarrow \Pred_{OT_{xy}}
-\land\, \alpha\!=\!\alpha_{xy} \land
-\Pred\,'_{{xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{xy}}}\Big)$.
+\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\!\!\bigvee_{y\in Y}\!\!\bigvee_{p\in P}\!\!
+\Big(\forall j.\vis{\beta_j}\!=\!\gamma_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
+\land\, \alpha\!=\!\alpha_{pxy} \land
+\Pred_{{s'\!,pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\Big)$.
   \end{small}

### 2018-07-18 2016-Weak-FH-Bisim/WeakBisim.tex
adding lemma
un peu de reorga et de redaction

@@
 
-\section{Notations}
-
+\section{Background and notations}
+This section introduces the notations we will use in this article, and  recalls the definition of pNets~\cite{henrio:Forte2016} with an informal semantics  of the pNet constructs.
 \subsubsection{Syntax and Notations}
-\TODO{copy pasted -- rearrange + move?}
 
@@
 (maps) over some countable indexed sets.   The indices will usually be
-integers, bounded or not. Such an indexed family is denoted as
+integers, bounded or not.
+We use indexed sets in pNets because we want to consider a set of processes, and provide an additional structure that explains how to synchronise them.
+Basically this could be done by tuples (but not by sets), however indexed sets are more general, can be infinite, and give a compact representation (the position is easier to express).
+
+An indexed family is denoted as
 follows: $a_i^{i\in I}$ is a family of elements $a_i$ indexed over the
@@
 To specify the set over which the structure is indexed, 
-indexed structures are always denoted with an exponent of the form $i\in I$
-(arithmetic only appears in the indexes if necessary).
+indexed structures are always denoted with an exponent of the form $i\in I$.
 Consequently, $a_i^{i\in I}$ defines first $I$ the set over which the
@@
 trivial).
-
-\section{Parameterised Networks (pNets): definition}
-\label{section:pnets}
-
-This section introduces pNets and the notations we will use in
-this paper. Then it gives the formal definition of pNet structures,
-together with an operational semantics for open pNets.
-
-pNets are tree-like structures, where the leaves are either
-\emph{parameterised labelled transition systems (pLTSs)}, expressing the
-behaviour of basic processes, or \emph{holes}, used as placeholders
-for unknown processes, of which we only specify the set of possible
-actions, this set is named the \emph{sort}.
-Nodes of the tree (pNet nodes) are synchronising artifacts, using a
-set of \emph{synchronisation vectors} that express the possible
-synchronisation between the parameterised actions of a subset of the
-sub-trees.
-
-%\LUDO{introduce magic op}
-%$\CreateISet{a}{i}$ creates a single entry indexed set $(i\mapsto a)$ \emph{but only if 
-%$a$ is not already an indexed set.}
 
@@
 naturally action terms will use data expressions as subterms.
-To be able to reason about the data flow between pLTSs, we
-distinguish \emph{input variables} of the form $?x$ within terms; the function
+
+We distinguish two kinds of parameterised actions: one that distinguishes input variables and one that does not. Let $a$
+range over action labels, $\symb{op}$ be operators, and $x_i$ range over
+variable names.
+
+We first define the set of actions that distinguish input variables, they will be used in the definition of \pLTS\ below:
+\[
+\begin{array}[l]{rcl@{\quad}p{5.5cm}}
+  \alpha\in\AlgA&::=&a(p_1,\ldots,p_n)&\text{action terms}\\
+  p_i&::=& ?x~|~\symb{Expr}&\text{parameters (input variable or expression)}\\
+  \symb{Expr}&::=& \symb{Value}~|~x~|~\symb{op}(\symb{Expr}_1,..,\symb{Expr}_n)&\text{Expressions}
+\end{array}
+\]
+The \emph{input variables} in an action term are those marked with a
+$\symb{?}$.
+We additionally suppose that each input variable does not
+appear somewhere else in the same action term:
+$p_i=?x\Rightarrow\forall j\neq i.\, x\notin \vars(p_j)$
+
+We first define the set of actions that do not distinguish input variables, they will be used in synchronisation vectors of pNets below:
+\[\begin{array}[l]{rcl@{\quad}l}
+  \alpha\in \AlgAS &::=&a(Expr_1,\ldots,Expr_n)
+\end{array}
+\]
+
+The function
 $\vars(t)$ identifies the set of variables in a term
@@
 $a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs), but it also allows
-for more general mechanisms, like gate negociation in Lotos, or broadcast
+for more general synchronisation mechanisms, like gate negociation in Lotos, or broadcast
 communications.
 
-\subsection{The (open) pNets Core Model}
-\label{section:pNets}
+\subsection{Parameterised Networks (pNets): definition}
+\label{section:pnets}
+
+This section introduces pNets and the notations we will use in
+this paper. Then it gives the formal definition of pNet structures,
+together with an operational semantics for open pNets.
+
+pNets are tree-like structures, where the leaves are either
+\emph{parameterised labelled transition systems (pLTSs)}, expressing the
+behaviour of basic processes, or \emph{holes}, used as placeholders
+for unknown processes, of which we only specify the set of possible
+actions, this set is named the \emph{sort}.
+Nodes of the tree (pNet nodes) are synchronising artifacts, using a
+set of \emph{synchronisation vectors} that express the possible
+synchronisation between the parameterised actions of a subset of the
+sub-trees.
+
+%\LUDO{introduce magic op}
+%$\CreateISet{a}{i}$ creates a single entry indexed set $(i\mapsto a)$ \emph{but only if 
+%$a$ is not already an indexed set.}
 
@@
 on finite branching of the transition relation.
-
-We first define the set of actions a pLTS can use, let $a$
-range over action labels, $\symb{op}$ are operators, and $x_i$ range over
-variable names. Action terms of \pLTS s are:
-\[
-\begin{array}[l]{rcl@{\quad}p{5.5cm}}
-  \alpha\in\AlgA&::=&a(p_1,\ldots,p_n)&\text{action terms}\\
-  p_i&::=& ?x~|~\symb{Expr}&\text{parameters (input variable or expression)}\\
-  \symb{Expr}&::=& \symb{Value}~|~x~|~\symb{op}(\symb{Expr}_1,..,\symb{Expr}_n)&\text{Expressions}
-\end{array}
-\]
-The input variables in an action term are those marked with a
-$\symb{?}$.
-We additionally suppose that each input variable does not
-appear somewhere else in the same action term:
-$p_i=?x\Rightarrow\forall j\neq i.\, x\notin \vars(p_j)$
 
@@
 exposes a single resulting global action.
-Actions involved at the pNet level (in the synchronisation vectors) do
-not need to distinguish  input 
-variables. Action terms used in synchronisation vectors of pNets are defined as follows:
-\[\begin{array}[l]{rcl@{\quad}l}
-  \alpha\in \AlgAS &::=&a(Expr_1,\ldots,Expr_n)
-\end{array}
-\]
 
@@
 \TODO{From Definition \ref{def:buildweakOT} we can prove following lemma that enables us to conclude FH-weak bisimulation coincides with  FH-bisimulation ... what does coincide mean here?}
+\begin{lemma}
+Let $A_1 = <J,\mathcal{S}_1, s_0,
+    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata.
+Let $<J,\mathcal{S}_1, s_0,
+    \WT_1>$ and $<J,\mathcal{S}_2,t_0,  \WT_2>$ be the
+weak open automata derived from $A_1$ and $A_2$ respectively.
+If $A_1$ and $A_2$ are weak FH-bisimilar then 
+\begin{itemize}
+ \item  For any weak open transition $wOT_1$ in $WT_1$:
+ \begin{mathpar}
+     \openrule
+         {
+           \gamma_j^{j\in J_1},\Pred_{OT_1},\Post_{OT_1}}
+         {s \OTWeakarrow {\alpha} s'}
+
+\end{mathpar}
+ there exists weak open transition $wOT_2$ in $WT_2$ :
+ \begin{mathpar}
+    \openrule
+         {
+           {\gamma\,'}_{j}^{j\in J_2}, \Pred_{OT_2},\Post_{OT_2}}
+         {t \OTWeakarrow {\alpha} t'}
+\end{mathpar}
+ such that  $J_1=J_{2}, (s'\!,t'|\Pred_{s',t'})\in \mathcal{R}$; 
+ and  \\
+ $\Pred_{s,t} \land \Pred_{OT_1}\\
+\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
+   \left( \forall j\in J_1. \gamma_j=\gamma'_{j}  \Rightarrow \Pred_{OT_2}
+     \land \alpha\!=\!\alpha_x \land  
+     \Pred_{s'\!,t'}\subst{\Post_{OT_1}}\subst{\Post_{OT_2}}\right)$
+
+\end{itemize}
+\end{lemma}
 

### 2018-07-19 2016-Weak-FH-Bisim/WeakBisim.tex
proof and lemma

--- 2018-07-09 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 \end{definition}
+
+We can rewrite a weak open transition  $ \OTWeakarrow {\alpha}$ as a sequence of open transitions $(\OTarrow{\tau})\!* (\OTarrow{\alpha})(\OTarrow{\tau})* $.
 
@@
 
-\TODO{From Definition \ref{def:buildweakOT} we can prove following lemma that enables us to conclude FH-weak bisimulation coincides with  FH-bisimulation ... what does coincide mean here?}
-
-\begin{lemma} \TODO{!!! formalisation of the lemma is cumbersome}
-$s (\OTarrow{\tau})\!\!* (\OTarrow{\alpha})(\OTarrow{\tau})\!\!* s'$ iff $s \OTWeakarrow {\alpha} s'$
-\end{lemma}
-
-\begin{proof} ($\Rightarrow$)
-
-\end{proof}
-
 \subsection{Weak FH-bisimulation}
@@
 proof in appendix
-
-----------------------------------------------
 
@@
 \subsection{Weak bisimulation is an equivalence}
+
+\begin{lemma} Let $A_1 = <J,\mathcal{S}_1, s_0,
+    \mathcal{T}_1>$ be open automata and $<J,\mathcal{S}_1, s_0,
+    \WT_1>$ be the
+weak open automata derived from $A_1$.
+
+\begin{itemize}
+ \item  For any weak open transition $\symb{WOT} \in \WT$:
+ \begin{mathpar}
+     \openrule
+         {
+           \gamma_j^{j\in J},\Pred_{OT},\Post_{OT}}
+         {s \OTWeakarrow {\alpha} s'}
+
+\end{mathpar}
+
+there exists  open transitions $\symb{OT} \in \mathcal{T}$:
+
+\begin{mathpar}
+     \openrule
+         {
+           \beta_j^{j\in J},\Pred_{OT},\Post_{OT}}
+         {s \OTarrow {\alpha} s'}
+
+\end{mathpar}
+ or $s=s'$ and $\alpha = \tau$
+\end{itemize}
+
+\begin{proof} 
+We can rewrite $s \OTWeakarrow {} s'$ as follows $s \OTarrow {} s_1 \OTarrow {} \ldots \OTarrow {} s_n  \OTarrow {} s'$, we proceed by induction on the length of the inference of  ${s \OTWeakarrow {\alpha} s'}$ (introduced in Definition \ref{def:buildweakOT}).
+First, if  $\overline{\gamma}=\emptyset$ then using rule (1) we can directly conclude  $s=s'$ and $\alpha =\tau$.
+Otherwise, using  rule (2)  we have  s $\OTarrow {\alpha} s'$ and forall $j$, $\gamma_j=\vis{\beta_j}$.
+Second, using rule (3)  we have ${s \OTWeakarrow {\alpha} s'}$ implies ${s \OTWeakarrow {\tau} s_1} \OTWeakarrow {\alpha} s_2  \OTWeakarrow {\tau} s'$ and forall $j$, $\gamma_j = \gamma_{1j}\,\dotcup\,\gamma_{2j}\,\dotcup\,\gamma_{3j}$, and by induction hypothesis this means that there exist $s, s'$  such that $ s \OTarrow {\alpha} s'$ and $j$, $\gamma_{2j}=\vis{\beta_j}$.
+\end{proof}   
+\end{lemma}
+
+\TODO{I am not sure that we have the same states between open auto and weak auto}
+
+Using this lemma, it is straightforward to see that....  
+\begin{lemma}
+Let $A_1 = <J,\mathcal{S}_1, s_0,
+    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata.
+Let $<J,\mathcal{S}_1, s_0,
+    \WT_1>$ and $<J,\mathcal{S}_2,t_0,  \WT_2>$ be the
+weak open automata derived from $A_1$ and $A_2$ respectively.
+If $A_1$ and $A_2$ are weak FH-bisimilar then 
+\begin{itemize}
+ \item  For any weak open transition $\symb{WOT} \in \WT_1$:
+ \begin{mathpar}
+     \openrule
+         {
+           \gamma_j^{j\in J},\Pred_{OT},\Post_{OT}}
+         {s \OTWeakarrow {\alpha} s'}
+
+\end{mathpar}
+
+there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
+ \begin{mathpar}
+    \openrule
+         {
+           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {t \OTWeakarrow {\alpha_x} t_x}
+\end{mathpar}
+ such that  $\forall x, J=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
+ and  \\
+ $\Pred \land \Pred_{OT}\\
+\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
+   \left( \forall j\in J_x. \gamma_j=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
+     \land \alpha\!=\!\alpha_x \land  
+     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
+
+\end{itemize}
+\end{lemma}
+
 \TODO{moved from body}

### 2018-07-19 2016-Weak-FH-Bisim/WeakBisim.tex

--- 2018-07-18 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
-\TODO{From Definition \ref{def:buildweakOT} we can prove following lemma that enables us to conclude FH-weak bisimulation coincides with  FH-bisimulation ... what does coincide mean here?}
-\begin{lemma}
-Let $A_1 = <J,\mathcal{S}_1, s_0,
-    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata.
-Let $<J,\mathcal{S}_1, s_0,
-    \WT_1>$ and $<J,\mathcal{S}_2,t_0,  \WT_2>$ be the
-weak open automata derived from $A_1$ and $A_2$ respectively.
-If $A_1$ and $A_2$ are weak FH-bisimilar then 
-\begin{itemize}
- \item  For any weak open transition $wOT_1$ in $WT_1$:
- \begin{mathpar}
-     \openrule
-         {
-           \gamma_j^{j\in J_1},\Pred_{OT_1},\Post_{OT_1}}
-         {s \OTWeakarrow {\alpha} s'}
-
-\end{mathpar}
- there exists weak open transition $wOT_2$ in $WT_2$ :
- \begin{mathpar}
-    \openrule
-         {
-           {\gamma\,'}_{j}^{j\in J_2}, \Pred_{OT_2},\Post_{OT_2}}
-         {t \OTWeakarrow {\alpha} t'}
-\end{mathpar}
- such that  $J_1=J_{2}, (s'\!,t'|\Pred_{s',t'})\in \mathcal{R}$; 
- and  \\
- $\Pred_{s,t} \land \Pred_{OT_1}\\
-\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-   \left( \forall j\in J_1. \gamma_j=\gamma'_{j}  \Rightarrow \Pred_{OT_2}
-     \land \alpha\!=\!\alpha_x \land  
-     \Pred_{s'\!,t'}\subst{\Post_{OT_1}}\subst{\Post_{OT_2}}\right)$
-
-\end{itemize}
-\end{lemma}
-
-\begin{lemma} \TODO{!!! formalisation of the lemma is cumbersome}
-$s (\OTarrow{\tau})\!\!* (\OTarrow{\alpha})(\OTarrow{\tau})\!\!* s'$ iff $s \OTWeakarrow {\alpha} s'$
-\end{lemma}
-
-\begin{proof} ($\Rightarrow$)
-
-\end{proof}
-
 \subsection{Weak FH-bisimulation}

### 2018-07-20 2016-Weak-FH-Bisim/WeakBisim.tex
Work on notations

--- 2018-07-18 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 This section introduces the notations we will use in this article, and  recalls the definition of pNets~\cite{henrio:Forte2016} with an informal semantics  of the pNet constructs.
-\subsubsection{Syntax and Notations}
+In general $x_i,y_i$ range over variables.
+\subsubsection*{Term algebra.}
+Our models rely on a notion of parameterised actions, that are
+symbolic expressions using data types and variables. As our model aims
+at encoding the low-level behaviour of possibly very different
+programming languages, we do not want to impose one specific algebra
+for denoting actions, nor any specific communication mechanism. So we
+leave unspecified the constructors of the algebra that will allow building
+expressions and actions. Moreover, we use a generic {\em action interaction}
+mechanism, based on (some sort of) unification between two or more action
+expressions, to express various kinds of communication or
+synchronisation mechanisms.
+
+\def\Talg{\mathcal{T}_{\Sigma}}
+\def\BoolExprs{\mathcal{B}}
+\def\Exprs{\mathcal{E}} \TODO{use Exprs}
+
+Formally, we assume the existence of a term algebra $\Talg$,
+where $\Sigma$ is the signature of the data and action constructors,
+and $\P$ a set of variables. Within $\Talg$, we distinguish a set of
+ expressions $\Exprs$, including a set of boolean
+expressions $\BoolExprs$ ($\BoolExprs\subseteq\Exprs$). We let $e_i$ range over expressions ($e_i\in\Exprs$).
+On top of $\mathcal{E}_\P$ we build the action algebra
+$\mathcal{A}_\P$, with $\mathcal{A}_P\subseteq\mathcal{T}_\P,
+\mathcal{E}_P\cap\mathcal{A}_P=\emptyset$;
+naturally action terms will use data expressions as subterms.
+
+We distinguish two kinds of parameterised actions: one that distinguishes input variables and one that does not. Let $a$
+range over action labels, $\symb{op}$ be operators, and $x_i$ range over
+variable names.
+
+We first define the set of actions that distinguish input variables, they will be used in the definition of \pLTS\ below:
+\[
+\begin{array}[l]{rcl@{\quad}p{5.5cm}}
+  \alpha\in\AlgA&::=&a(p_1,\ldots,p_n)&\text{action terms}\\
+  p_i&::=& ?x~|~e_i&\text{parameters (input variable or expression)}\\
+  e_i&::=& \symb{Value}~|~x~|~\symb{op}(\symb{e}_1,..,\symb{e}_n)&\text{Expressions}
+\end{array}
+\]
+The \emph{input variables} in an action term are those marked with a
+$\symb{?}$.
+We additionally suppose that each input variable does not
+appear somewhere else in the same action term:
+$p_i=?x\Rightarrow\forall j\neq i.\, x\notin \vars(p_j)$
+
+The set of actions that do not distinguish input variables is denoted $\AlgAS$, it will be used in synchronisation vectors of pNets below:
+\[\begin{array}[l]{rcl@{\quad}l}
+  \alpha\in \AlgAS &::=&a(e_1,\ldots,e_n)
+\end{array}
+\]
+
+The function
+$\vars(t)$ identifies the set of variables in a term
+$t\in\AlgT$, and $iv(t)$ returns its input variables.
+Action algebras can encode naturally usual point-to-point message passing calculi (using 
+$a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs), but it also allows
+for more general synchronisation mechanisms, like gate negociation in Lotos, or broadcast
+communications.
+
+\smallskip
+
+We denote $y\gets x$ a substitution. The application of the substitution is denoted
+$\subst{y\gets x}$, the operation replaces in a term all occurrences 
+of the term $y$ by the term $x$ (note that the absence of binders makes this operation 
+trivial). 
+We use sets of equations of the form $x_i=e_i$, ranged over by $\Post$; $\subst{\Post}$ is the substitution that applies all the substitutions defined by $\Post$.
+
+\subsubsection*{Notations: indexed sets and substitution}
 
@@
 A_i^{i\in I}$'' to mean $\exists i\in I.\, x=A_i$.
-An empty family is denoted $[]$. % (it can be defined as $a_i^{i\in\emptyset}$).
+%An empty family is denoted $[]$. % (it can be defined as $a_i^{i\in\emptyset}$).
 To simplify equations, an indexed set can be denoted $\set{M}$
@@
 joined families.
-We suppose here that disjoint unions are always well defined; this
-requires to choose disjoint  
-indices in the definition of the component system (e.g. name of
-methods of different interfaces).
-We denote $y\gets x$ a substitution. The application of the substitution is denoted
-$\subst{y\gets x}$, the operation replaces in a term all occurrences 
-of the term $y$ by the term $x$ (note that the absence of binders makes this operation 
-trivial).
-
-%\smallskip\noindent
-\paragraph*{Notations.}
-We extensively use indexed structures
-over some countable indexed sets, which are equivalent to mappings over
-the countable set. % . The indexes will usually be
-% integers, bounded or not. Such an indexed family is
-%denoted
-%follows:
-$a_i^{i\in I}$
-%, or equivalently  $(i\mapsto a_i)^{i\in I}$
-denotes a family of elements $a_i$ indexed over the
-set $I$. % Such a family
-% is equivalent to the mapping $(i\mapsto a_i)^{i\in I}$.
-% To specify the set over which the structure is indexed,
-% indexed structures are always denoted with an exponent of the form $i\in I$
-% (arithmetic only appears in the indexes if necessary).
-$a_i^{i\in I}$ defines both $I$ the set over which the family is
-indexed (called \emph{range}), and $a_i$ the elements of the family.
-E.g., $a^{i\in\{3\}}$ is the mapping with a single entry $a$ at index
-$3$ ; abbreviated $(3\mapsto a)$ in the following.
-When this is not
-ambiguous, we shall use notations for sets, and typically write
-``indexed set over I'' when formally we should speak of multisets, and
-write $x\in a_i^{i\in I}$ to mean $\exists i\in I.\, x=a_i$.  An empty
-family is denoted $\emptyset$. We
-denote classically with an overline -- $\overline{a}$  -- a family when the indexing set 
-is
-not meaningful.  $\uplus$ is the disjoint union on
-indexed sets.
-
-\paragraph*{Term algebra.}
-Our models rely on a notion of parameterised actions, that are
-symbolic expressions using data types and variables. As our model aims
-at encoding the low-level behaviour of possibly very different
-programming languages, we do not want to impose one specific algebra
-for denoting actions, nor any specific communication mechanism. So we
-leave unspecified the constructors of the algebra that will allow building
-expressions and actions. Moreover, we use a generic {\em action interaction}
-mechanism, based on (some sort of) unification between two or more action
-expressions, to express various kinds of communication or
-synchronisation mechanisms.
-
-\def\Talg{\mathcal{T}_{\Sigma,\P}}
-\def\BoolExprs{\mathcal{B}_{\P}}
-Formally, we assume the existence of a term algebra $\Talg$,
-where $\Sigma$ is the signature of the data and action constructors,
-and $\P$ a set of variables. Within $\Talg$, we distinguish a set of
-data expressions $\mathcal{E}_\P$, including a set of boolean
-expressions $\BoolExprs$ ($\BoolExprs\subseteq\mathcal{E}_\P$).
-On top of $\mathcal{E}_\P$ we build the action algebra
-$\mathcal{A}_\P$, with $\mathcal{A}_P\subseteq\mathcal{T}_\P,
-\mathcal{E}_P\cap\mathcal{A}_P=\emptyset$;
-naturally action terms will use data expressions as subterms.
-
-We distinguish two kinds of parameterised actions: one that distinguishes input variables and one that does not. Let $a$
-range over action labels, $\symb{op}$ be operators, and $x_i$ range over
-variable names.
-
-We first define the set of actions that distinguish input variables, they will be used in the definition of \pLTS\ below:
-\[
-\begin{array}[l]{rcl@{\quad}p{5.5cm}}
-  \alpha\in\AlgA&::=&a(p_1,\ldots,p_n)&\text{action terms}\\
-  p_i&::=& ?x~|~\symb{Expr}&\text{parameters (input variable or expression)}\\
-  \symb{Expr}&::=& \symb{Value}~|~x~|~\symb{op}(\symb{Expr}_1,..,\symb{Expr}_n)&\text{Expressions}
-\end{array}
-\]
-The \emph{input variables} in an action term are those marked with a
-$\symb{?}$.
-We additionally suppose that each input variable does not
-appear somewhere else in the same action term:
-$p_i=?x\Rightarrow\forall j\neq i.\, x\notin \vars(p_j)$
-
-We first define the set of actions that do not distinguish input variables, they will be used in synchronisation vectors of pNets below:
-\[\begin{array}[l]{rcl@{\quad}l}
-  \alpha\in \AlgAS &::=&a(Expr_1,\ldots,Expr_n)
-\end{array}
-\]
-
-The function
-$\vars(t)$ identifies the set of variables in a term
-$t\in\AlgT$, and $iv(t)$ returns its input variables.
-Action algebras can encode naturally usual point-to-point message passing calculi (using 
-$a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs), but it also allows
-for more general synchronisation mechanisms, like gate negociation in Lotos, or broadcast
-communications.
-
-\subsection{Parameterised Networks (pNets): definition}
+%We suppose here that disjoint unions are always well defined; this
+%requires to choose disjoint  
+%indices in the definition of the component system (e.g. name of
+%methods of different interfaces).
+$\setminus$ is the standard subtraction operation on sets.
+
+%%\smallskip\noindent
+%\paragraph*{Indexed sets.}
+%We extensively use indexed structures
+%over some countable indexed sets, which are equivalent to mappings over
+%the countable set. % . The indexes will usually be
+%% integers, bounded or not. Such an indexed family is
+%%denoted
+%%follows:
+%$a_i^{i\in I}$
+%%, or equivalently  $(i\mapsto a_i)^{i\in I}$
+%denotes a family of elements $a_i$ indexed over the
+%set $I$. % Such a family
+%% is equivalent to the mapping $(i\mapsto a_i)^{i\in I}$.
+%% To specify the set over which the structure is indexed,
+%% indexed structures are always denoted with an exponent of the form $i\in I$
+%% (arithmetic only appears in the indexes if necessary).
+%$a_i^{i\in I}$ defines both $I$ the set over which the family is
+%indexed (called \emph{range}), and $a_i$ the elements of the family.
+%E.g., $a^{i\in\{3\}}$ is the mapping with a single entry $a$ at index
+%$3$ ; abbreviated $(3\mapsto a)$ in the following.
+%When this is not
+%ambiguous, we shall use notations for sets, and typically write
+%``indexed set over I'' when formally we should speak of multisets, and
+%write $x\in a_i^{i\in I}$ to mean $\exists i\in I.\, x=a_i$.  An empty
+%family is denoted $\emptyset$. We
+%denote classically with an overline -- $\overline{a}$  -- a family when the indexing set 
+%is
+%not meaningful.  $\uplus$ is the disjoint union on
+%indexed sets.
+
+\subsection{Parameterised Networks (pNets)}
 \label{section:pnets}
-
-This section introduces pNets and the notations we will use in
-this paper. Then it gives the formal definition of pNet structures,
-together with an operational semantics for open pNets.
 
@@
 where $\alpha \in\AlgA$ is a parameterised action, $e_b \in
-\AlgB$ is a guard, and the variables $x_j\in P$
+\AlgB$ is a guard, and the variables $x_j\in P$ \TODO{P?}
 are assigned the expressions $e_j\in \AlgE$.

### 2018-07-24 2016-Weak-FH-Bisim/WeakBisim.tex
s'' -> s'
adding lemma...

@@
 \newcommand{\coloncolon}{{:\hspace{-.2ex}:}}
+\newcommand{\bigcupdot}{\charfusion[\mathop]{\bigcup}{\cdot}}
 \makeatletter
@@
 prove that it is decidable whether a relation is a 
-FH-bisimulation, provided the logic of the predicates is decidable (see
-\cite{henrio:Forte2016}).
+FH-bisimulation, provided the logic of the predicates is decidable (see \cite{henrio:Forte2016}).
 
@@
 FH-bisimulation. More precisely, one can define two preservation
-properties, namely 1) when one hole of a pNet is filled by two bisimilar
-other (open) pNets; and 2) when the same hole in two bisimilar pNets are
+properties, namely 1) when one hole of a pNet is filled by two bisimilar other (open) pNets; and 2) when the same hole in two bisimilar pNets are
 filled by the same pNet, in other words, composing a pNet with two
@@
            \vis{\overline{\beta}}\!,\Pred,\Post
-				 } {s \OTWeakarrow {\alpha} s''} \in \WT
+				 } {s \OTWeakarrow {\alpha} s'} \in \WT
 }
@@
 
-\TODO{I am not sure that we have the same states between open auto and weak auto}
-
+\TODO{I am not sure that we have the same states between open auto 
+and weak auto}
+
+\begin{lemma} Let $A = <J,\mathcal{S}, s_0,
+    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
+    \WT>$ be the
+weak open automata derived from $A$.
+
+\begin{mathpar}
+  \mprset {vskip=.5ex}
+\inferrule {\openrule
+         {
+           \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
+         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}
+\qquad
+\openrule
+         {
+           \overline{\beta^2_i},\Pred^2_i,\Post^2_i  }
+         {s^2_i \OTarrow {\alpha} s^2_{i+1}} \in \mathcal{T}
+\qquad
+\openrule
+         {
+           \overline{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
+         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
+\\
+s=s^1_i \wedge s^1_n=s^2_0 \wedge s^2_n = s^3_0 \wedge s^3_n=s'
+\\\\
+\overline{\gamma}=\biguplus_{i=0}^n \vis{\overline{\beta^1_i}} \dotcup  \biguplus_{i=0}^n \vis{\overline{\beta^2_i}} \dotcup \biguplus_{i=0}^n \vis{\overline{\beta^3_i}}
+\\
+\Pred=\bigwedge_{i}^n\Pred^1_i\land\bigwedge_{i}^n\Pred^2_i\subst{\Post_1}\land (\bigwedge_{i}^n\Pred^3_i\subst{\Post^2_i})\subst{\Post^1_i}
+}
+{
+\openrule
+         {
+           \overline{\gamma},
+		\Pred,
+				({x^3_k\gets (e^3_k\subst {\Post^2_i})\subst{\Post^1_i}})^{k\in K} } 
+         {s \OTWeakarrow {\alpha} s'} \in\WT
+}
+\end{mathpar}
+\end{lemma}
+
+\begin{proof} 
+We proceed by induction on the depth of the derivation tree with with we  build  a weak transition (introduced in Definition \ref{def:buildweakOT}).
+The base cases  are:
+\begin{itemize}
+\item $n=0$, then we have by rule (1)
+\begin{mathpar}
+     \openrule
+         {
+           \emptyset,\symb{True},\symb{Id}(s)}
+         {s \OTWeakarrow {\tau} s}
+         \in \WT
+
+\end{mathpar}  
+\item $n=1$, then by rule (2) we have:
+\begin{mathpar}
+ % \mprset {vskip=.5ex}
+\inferrule{
+ \openrule
+         {
+           \overline{\beta},\Pred,\Post}
+         {s \OTarrow {\alpha} s'} \in \mathcal{T}
+}
+{ \openrule
+         {
+           \vis{\overline{\beta}}\!,\Pred,\Post
+				 } {s \OTWeakarrow {\alpha} s'} \in \WT
+}
+\end{mathpar}
+\end{itemize}
+For the inductive step, first we have by induction hypothesis that
+\begin{mathpar}
+{ \openrule
+         {
+           \overline{\gamma}\!,\Pred,\Post
+				 } {s \OTWeakarrow {\alpha} s'} \in \WT
+}
+\end{mathpar}
+\end{proof}
 Using this lemma, it is straightforward to see that....  

### 2018-07-24 2016-Weak-FH-Bisim/WeakBisim.tex
algebras

--- 2018-07-20 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
-\def\Talg{\mathcal{T}_{\Sigma}}
-\def\BoolExprs{\mathcal{B}}
-\def\Exprs{\mathcal{E}} \TODO{use Exprs}
-
-Formally, we assume the existence of a term algebra $\Talg$,
-where $\Sigma$ is the signature of the data and action constructors,
-and $\P$ a set of variables. Within $\Talg$, we distinguish a set of
- expressions $\Exprs$, including a set of boolean
-expressions $\BoolExprs$ ($\BoolExprs\subseteq\Exprs$). We let $e_i$ range over expressions ($e_i\in\Exprs$).
-On top of $\mathcal{E}_\P$ we build the action algebra
-$\mathcal{A}_\P$, with $\mathcal{A}_P\subseteq\mathcal{T}_\P,
-\mathcal{E}_P\cap\mathcal{A}_P=\emptyset$;
+%\def\Talg{\mathcal{T}_{\Sigma}}
+%\def\BoolExprs{\mathcal{B}}
+%\def\Exprs{\mathcal{E}} \TODO{use Exprs}
+%\def\Actionalg{\mathcal{A}}
+
+Formally, we assume the existence of a term algebra $\AlgT$,
+where $\Sigma$ is the signature of the data and action constructors. Within $\AlgT$, we distinguish a set of
+ expressions $\AlgE$, including a set of boolean
+expressions $\AlgE$ ($\AlgB\subseteq\AlgE$). We let $e_i$ range over expressions ($e_i\in\AlgE$).
+On top of $\AlgE$ we build the action algebra
+$\AlgA$, with $\AlgA\subseteq\AlgT,
+\AlgE\cap\AlgA=\emptyset$;
 naturally action terms will use data expressions as subterms.
@@
 
-We denote $y\gets x$ a substitution. The application of the substitution is denoted
-$\subst{y\gets x}$, the operation replaces in a term all occurrences 
-of the term $y$ by the term $x$ (note that the absence of binders makes this operation 
+We denote $y\gets e$ a substitution. The application of the substitution is denoted
+$\subst{y\gets e}$, the operation replaces in a term all occurrences 
+of the variable $y$ by the expression $e$ (note that the absence of binders makes this operation 
 trivial). 
@@
 
-In the following definitions, we extensively use indexed structures
-(maps) over some countable indexed sets.   The indices will usually be
+In this article, we extensively use indexed structures
+(maps) over some countable indexed sets.   The indices can typically be
 integers, bounded or not.
-We use indexed sets in pNets because we want to consider a set of processes, and provide an additional structure that explains how to synchronise them.
-Basically this could be done by tuples (but not by sets), however indexed sets are more general, can be infinite, and give a compact representation (the position is easier to express).
+We use indexed sets in pNets because we want to consider a set of processes, and specify separately how to synchronise them.
+Roughly this could also be realised using tuples, however indexed sets are more general, can be infinite, and give a compact representation than using the position in a possibly long tuple.
 
@@
 
-\subsection{Parameterised Networks (pNets)}
+\subsection*{Parameterised Networks (pNets)}
 \label{section:pnets}
@@
 behaviour of basic processes, or \emph{holes}, used as placeholders
-for unknown processes, of which we only specify the set of possible
-actions, this set is named the \emph{sort}.
+for unknown processes. 
+%, of which we only specify the set of possible
+%actions, this set is named the \emph{sort}.
 Nodes of the tree (pNet nodes) are synchronising artifacts, using a
@@
 A pLTS is a labelled transition system with variables; variables can be
-manipulated, defined, or accessed inside states, actions, guards, and
+used inside states, actions, guards, and
 assignments. Without loss of generality and to simplify the formalisation, we suppose 
-here that variables are local to each 
-state: each state has its set of variables disjoint from the others. Transmitting 
-variable values from one state to the other can be done by explicit assignment. 
+ that variables are local to each 
+state: each state has its set of variables disjoint from the ones of the other states. Transmitting the value of
+variables from one state to another can be done by explicit assignment. 
 %Similarly, to simplify the management of variables and without loss of expressivity, we 
@@
 where $\alpha \in\AlgA$ is a parameterised action, $e_b \in
-\AlgB$ is a guard, and the variables $x_j\in P$ \TODO{P?}
+\AlgB$ is a guard, and the variables $x_j$ 
 are assigned the expressions $e_j\in \AlgE$.
@@
 inference rule. They correspond to two different logical levels.
- The open transition is itself a logical implication, but using a simple logic (this logic includes the boolean expressions $\BoolExprs$, boolean operators, and term equality).
+ The open transition is itself a logical implication, but using a simple logic (this logic includes the boolean expressions $\AlgB$, boolean operators, and term equality).
 We differentiate classical (black) inference rules that use

### 2018-07-24 2016-Weak-FH-Bisim/WeakBisim.tex
reorganisation de section

@@
 
-\section{Status and TODO list}
+\section*{Status and TODO list}
 TODOS et deadline
@@
 \begin{itemize}
-\item reorga sec weak bisim + thm -> 10 Juil
+\item[X] reorga sec weak bisim + thm -> 10 Juil
 \item  intro et orga globale du papier -> fin aout
@@
 In general $x_i,y_i$ range over variables.
+
+\subsection{Notations}
 \subsubsection*{Term algebra.}
@@
 
-\subsubsection*{Notations: indexed sets and substitution}
+\subsubsection*{Indexed sets and substitution}
 
@@
 
-\subsection*{Parameterised Networks (pNets)}
+\subsection{Parameterised Networks (pNets)}
 \label{section:pnets}
@@
 $\vars(e_k)\subseteq \bigcup_{l\in I_k\uplus J_k}{\vars({\alpha_l})}$.
-
 \end{itemize}
+Synchronisation vectors are identified modulo renaming of variables that appear in their 
+action terms.
 \end{definition}
@@
 \end{itemize}
-\end{definition}
-
-Synchronisation vectors are identified modulo renaming of variables that appear in their 
-action terms.
 
@@
 is said to be \emph{open}.
+\end{definition}
+
+\TODO{informal semantics of pnets}
 
@@
 
-\section{Running Example}
+\subsection{Running Example}
 To illustrate this work, we use the well-known Alternate bit protocol

### 2018-07-24 2016-Weak-FH-Bisim/WeakBisim.tex
reorga OT  / pnets et un peu de texte

@@
 % !TEX TS-program = pdflatex
+% !TeX spellcheck = en_GB
 
@@
 \paragraph{Contribution}
+The main interest of our symbolic approach is to define a method to
+prove properties directly on open structures, that will be preserved
+by any correct instantiation of the holes.
 
@@
 
-\TODO{informal semantics of pnets}
+The informal semantics of \pNet s is as follows.
+\pLTS s behave more or less like  classical automata with conditional branching and variables.
+The actions on the \pLTS s can send or receive values, potentially modifying the value of variables.
+\pNet s are synchronisation entities: a \pNet composes several subnets and  synchronisation vectors define how the subnets interact, where a subnet is either a \pNet or a \pLTS.
+Synchronisation between subnets is defined by synchronisation vectors that express how an action of a subnet can be synchronised with actions of other subnet, and how the resulting synchronised action is visible to the outside of the \pNet.
+Synchronisation vectors also allow to explicitly export an action of a subnet to the next level, or to allow to subnets to synchronise and only exporting a non0observable action (provided such an non-visible action labels exist in the action algebra.
+Finally, a \pNet can leave subnets undefined and instead declare holes with a well-defined signature.
+Holes can then be filled with a subnet.
+This is defined as follows.
+
+\begin{definition}[pNet composition]
+	An open pNet: $\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
+	\overline{\symb{SV}}\myrangle$
+ can be (partially) filled by providing  a pNets $\pNet'$ of the
+	right sort to fill one of  its holes.	
+	Suppose $j_0\in J$:
+	%% \[\mylangle \pNet_i^{i\in I},S_j^{j\in J}, \symb{SV}_k^{k\in
+	%%   K}\myrangle\left[(\pNet'_i)^{i\in L}\right]= \mylangle \pNet_i^{i\in
+	%%   I}\left[(\pNet'_i)^{i\in L}\right]\uplus(\pNet'_i)^{i\in J\cap L},S_j^{j\in 
+	%%J\setminus L},
+	%% \symb{SV}_k^{k\in K}\myrangle
+	%% \]
+	\[\pNet\left[\pNet'\right]_{j_0}= \mylangle 
+	\pNet_i^{i\in I}\uplus\{j_0\mapsto \pNet'\},\Sort_j^{j\in J\setminus \{j_0\}},
+	\overline{\symb{SV}}\myrangle
+	\]
+\end{definition}
 
@@
 
-\section{Operational Semantics for Open pNets}
-\label{section:op-semantics}
-
-The semantics of open pNets will be defined  as an open automaton. An open
+\subsection{Open Automata: A model of process composition}
+\label{sec:OT}
+
+The semantics of open \pNet s will be defined  as an open automaton. An open
 automaton is an automaton where each transition composes transitions of several LTSs with
@@
 set of state modifications.
+This section defines open automata and a bisimulation theory for them.
+Open automata are not composition structures but they are made of transitions that are dependent of the actions of the holes, and they can reason on variables (potentially with only symbolic values).
 %\TODO{adopt a uniform notation for open transitions, almost each instance has a 
@@
 
+An open automaton is then simply an automaton where each transition is an open transition.
 \begin{definition}[Open automaton]
@@
 \end{definition}
+
+\subsection{Bisimulation for open Automata}
+\label{section:bisimulation}
+
+The equivalence we need is a strong bisimulation between
+pNets having exactly the same Holes with the same sorts, but using a
+flexible matching 
+between open transition, to accommodate comparisons between pNet
+expressions with different architectures.
+
+We define now a bisimulaiton relation adapted to open automata and their parametric nature.
+The relation relates states of the open automaton and states equivalence between the open transitions between the states.
+Its key characteristics are 1) the introduction of predicates in the bisimulation relation: as states may contain variables, relation between states may depend on the value of the variables; 2) the bisimulation property relates elements of the open transitions and take into account predicates over variables, actions of the holes, and state modifications.
+ We name it FH-bisimulation,
+ as a short cut for the ``Formal Hypotheses'' manipulated in the
+ transitions, but also as a reference to the work of De Simone~\cite{deSimone85},
+ that pioneered this idea.
+
+Let $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$ be a relation over the set $\mathcal{S}_1$ and 
+$\mathcal{S}_2$ constrained by a predicate
+More precisely, for any pair $(s,t)$, there is a 
+   single
+      $(s,t|\Pred_{s,t})\in\mathcal{R}$  stating that $s$ and $t$ are related 
+      if $\Pred_{s,t}$       is 
+      true, i.e. the states are related when the variables in $s$ and $t$ verify the 
+      predicate $\Pred_{s,t}$.
+ FH-bisimulation is defined formally: 
+ \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim}
+
+\noindent
+\begin{minipage}{0.69\linewidth} 	Suppose that
+   $A_1 = <\!J,\mathcal{S}_1, s_0,
+   \mathcal{T}_1\!>$ and $A_2 = <\!J,\mathcal{S}_2,t_0, \mathcal{T}_2\!>$
+   are open automata with identical holes of the same sort.
+
+ Then 
+$\mathcal{R}$ is an FH-bisimulation iff for any  states
+$s\in\mathcal{S}_1$ and $t\in\mathcal{S}_2$, $(s,t|\Pred_{s,t})\in\mathcal{R}$, we 
+have
+the following:
+\end{minipage}
+\hspace{2mm}
+\begin{minipage}{0.30\linewidth}
+	\includegraphics[width=\linewidth]{XFIG/Bisim}
+%	\TODO{J'ai ajoute les predicats. Il reste a dessiner la ``couverture'' si j'y arrive...}
+\end{minipage}
+
+ \begin{itemize}
+ \item  For any open transition $OT$ in $\mathcal{T}_1$:
+ \begin{mathpar}
+     \openrule
+         {
+           \beta_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
+         {s \OTarrow {\alpha} s'}
+
+\end{mathpar}
+ there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
+ \begin{mathpar}
+%    \left( fresh \ \overline{\alpha_i}, \overline{b_j}, v_x.\ \
+    \openrule
+         {
+           \beta_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {t \OTarrow {\alpha_x} t_x}
+%         \right)
+\end{mathpar}
+ such that  $\forall x, J_1=J_{x}, \exists \Pred_{s',t_x}. (s',t_x|\Pred_{s',t_x})\in 
+ \mathcal{R}$; 
+ and  \\
+ $\Pred_{s,t} \land \Pred_{OT}\\
+\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
+   \left( \forall j. \beta_j=\beta_{jx}  \Rightarrow \Pred_{OT_x}
+     \land \alpha\!=\!\alpha_x \land  
+     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
+     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
+     %     \right)$.
+
+%     \TODO{Eric: j'ai ajoute $\exists$ sur les predicats $\Pred_{s',t_x}$, qui n'etaient pas definis...}
+
+ \item  and symmetrically any open transition from $t$ in $\mathcal{T}_2$ can be 
+      covered by a set of transitions from $s$ in $\mathcal{T}_1$.
+ \end{itemize}
+
+% \TODO{Eric: il reste des petits bugs genre $s^{2'}_x$ plutot que
+%   $s^{2}_x$}
+
+%Where $\symb{Subst}(\Pred,\Post)$ is the parallel substitution of all
+%assigned variables.
+
+% \TODO{do we want formulas for this?}
+ \end{definition}
+Classically, $\Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}$
+applies in parallel the  
+substitutions $\Post_{OT}$ and $\Post_{OT_x}$ (parallelism is crucial
+inside each $\Post$ set but not between  $\Post_{OT}$ and
+$\Post_{OT_x}$ that are independent), applying the assignments of the involved rules.
+We can prove that such a bisimulation si an equivalence relation:
+
+\begin{theorem}[FH-Bisimulation is an equivalence]\label{thm-equiv} Suppose $\mathcal{R}$ 
+is an FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
+reflexive, symmetric and transitive.
+
+\end{theorem}
+
+\medskip
+
+If we assume that everything is finite (states and transitions in the
+open automata, and the predicates in $\mathcal{R}$, then it is easy to
+prove that it is decidable whether a relation is a 
+FH-bisimulation, provided the logic of the predicates is decidable (see \cite{henrio:Forte2016}).
+
+\begin{theorem}[Decidability of FH-bisimulation]
+Let $A_1$ and $A_2$ be finite open automata
+and $\mathcal{R}$ a relation over their states $\mathcal{S}_1$ and
+$\mathcal{S}_2$ constrained by a finite set of predicates. Assume that
+the predicates inclusion is decidable over  
+the action algebra $\mathcal{A}_P$. Then it is decidable whether the relation 
+$\mathcal{R}$ is a FH-bisimulation.
+
+\end{theorem}
+
+\section{Operational Semantics for Open pNets}
+\label{section:op-semantics}
 
@@
 \subsection{Computing and using open automata}
+\TODO{REMOVE?}
 In this section we present a simple algorithm to construct the open
@@
 
-\section{Bisimulation}
-\label{section:bisimulation}
-
-	Now we use our symbolic operational semantics to define a notion of
-	strong (symbolic) bisimulation. Moreover this equivalence is decidable whenever we 
-	have some
-	decision procedure on the predicates of the action algebra.
-
-%% , that we prove compatible with the
-%% composition of open pNets. \TODO{do we really know this ?}
-
-The equivalence we need is a strong bisimulation between
-pNets having exactly the same Holes with the same sorts, but using a
-flexible matching 
-between open transition, to accommodate comparisons between pNet
-expressions with different architectures.
- We name it FH-bisimulation,
- as a short cut for the ``Formal Hypotheses'' manipulated in the
- transitions, but also as a reference to the work of De Simone~\cite{deSimone85},
- that pioneered this idea.
-
-Let $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$ be a relation over the set $\mathcal{S}_1$ and 
-$\mathcal{S}_2$ constrained by a predicate
-More precisely, for any pair $(s,t)$, there is a 
-   single
-      $(s,t|\Pred_{s,t})\in\mathcal{R}$  stating that $s$ and $t$ are related 
-      if $\Pred_{s,t}$ 
-      is 
-      true, i.e. the states are related when the variables in $s$ and $t$ verify the 
-      predicate $\Pred_{s,t}$.
- FH-bisimulation is defined formally: 
- \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim}
-
-\noindent
-\begin{minipage}{0.69\linewidth} 	Suppose that
-   $A_1 = <\!J,\mathcal{S}_1, s_0,
-   \mathcal{T}_1\!>$ and $A_2 = <\!J,\mathcal{S}_2,t_0, \mathcal{T}_2\!>$
-   are open automata with identical holes of the same sort.
-
- Then 
-$\mathcal{R}$ is an FH-bisimulation iff for any  states
-$s\in\mathcal{S}_1$ and $t\in\mathcal{S}_2$, $(s,t|\Pred_{s,t})\in\mathcal{R}$, we 
-have
-the following:
-\end{minipage}
-\hspace{2mm}
-\begin{minipage}{0.30\linewidth}
-	\includegraphics[width=\linewidth]{XFIG/Bisim}
-%	\TODO{J'ai ajoute les predicats. Il reste a dessiner la ``couverture'' si j'y arrive...}
-\end{minipage}
-
- \begin{itemize}
- \item  For any open transition $OT$ in $\mathcal{T}_1$:
- \begin{mathpar}
-     \openrule
-         {
-           \beta_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
-         {s \OTarrow {\alpha} s'}
-
-\end{mathpar}
- there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
- \begin{mathpar}
-%    \left( fresh \ \overline{\alpha_i}, \overline{b_j}, v_x.\ \
-    \openrule
-         {
-           \beta_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {t \OTarrow {\alpha_x} t_x}
-%         \right)
-\end{mathpar}
- such that  $\forall x, J_1=J_{x}, \exists \Pred_{s',t_x}. (s',t_x|\Pred_{s',t_x})\in 
- \mathcal{R}$; 
- and  \\
- $\Pred_{s,t} \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-   \left( \forall j. \beta_j=\beta_{jx}  \Rightarrow \Pred_{OT_x}
-     \land \alpha\!=\!\alpha_x \land  
-     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
-     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
-     %     \right)$.
-
-%     \TODO{Eric: j'ai ajoute $\exists$ sur les predicats $\Pred_{s',t_x}$, qui n'etaient pas definis...}
-
- \item  and symmetrically any open transition from $t$ in $\mathcal{T}_2$ can be 
-      covered by a set of transitions from $s$ in $\mathcal{T}_1$.
- \end{itemize}
-
-% \TODO{Eric: il reste des petits bugs genre $s^{2'}_x$ plutot que
-%   $s^{2}_x$}
-
-%Where $\symb{Subst}(\Pred,\Post)$ is the parallel substitution of all
-%assigned variables.
+\subsection{Bisimulation for open \pNet s and Composability}
+\label{section:bisimulation-PN}
+As  our symbolic operational semantics provides an open automaton, we can apply the notion of
+	strong (symbolic) bisimulation on automata to open \pNet s:
+\begin{definition}[FH-bisimulation for open \pNet s]\label{def:bisim-pnets}
 Two pNets are FH-bisimilar if there exist a relation between their associated 
@@
 the predicate associated to the relation between the initial states is true.
-% \TODO{do we want formulas for this?}
 \end{definition}
-Classically, $\Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}$
-applies in parallel the  
-substitutions $\Post_{OT}$ and $\Post_{OT_x}$ (parallelism is crucial
-inside each $\Post$ set but not between  $\Post_{OT}$ and
-$\Post_{OT_x}$ that are independent), applying the assignments of the involved rules.
-
-\medskip
-If we assume that everything is finite (states and transitions in the
-open automata, and the predicates in $\mathcal{R}$, then it is easy to
-prove that it is decidable whether a relation is a 
-FH-bisimulation, provided the logic of the predicates is decidable (see \cite{henrio:Forte2016}).
-
-\begin{theorem}[Decidability of FH-bisimulation]
-Let $A_1$ and $A_2$ be finite open automata
-and $\mathcal{R}$ a relation over their states $\mathcal{S}_1$ and
-$\mathcal{S}_2$ constrained by a finite set of predicates. Assume that
-the predicates inclusion is decidable over  
-the action algebra $\mathcal{A}_P$. Then it is decidable whether the relation 
-$\mathcal{R}$ is a FH-bisimulation.
-
-\end{theorem}
-
-\section{Composability}
-
-The main interest of our symbolic approach is to define a method to
-prove properties directly on open structures, that will be preserved
-by any correct instantiation of the holes. In this section we define a
-composition operator for open pNets, and we prove that it preserves
+We can now prove that \pNet\ composition  preserves
 FH-bisimulation. More precisely, one can define two preservation
-properties, namely 1) when one hole of a pNet is filled by two bisimilar other (open) pNets; and 2) when the same hole in two bisimilar pNets are
+properties, namely 1) when one hole of a \pNet\ is filled by two bisimilar other (open) pNets; and 2) when the same hole in two bisimilar pNets are
 filled by the same pNet, in other words, composing a pNet with two
 bisimilar contexts. The general case will be obtained by
-transitivity of the bisimulation relation. We concentrate here on the
-second property, that is the most interesting.
-
-\begin{theorem}[FH-Bisimulation is an equivalence]\label{thm-equiv} Suppose $\mathcal{R}$ 
-is an FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
-reflexive, symmetric and transitive.
-
-\end{theorem}
-
-\begin{definition}[pNet composition]
-	An open pNet: $\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
-	\overline{\symb{SV}}\myrangle$
- can be (partially) filled by providing  a pNets $\pNet'$ of the
-	right sort to fill one of  its holes.	
-	Suppose $j_0\in J$:
-	%% \[\mylangle \pNet_i^{i\in I},S_j^{j\in J}, \symb{SV}_k^{k\in
-	%%   K}\myrangle\left[(\pNet'_i)^{i\in L}\right]= \mylangle \pNet_i^{i\in
-	%%   I}\left[(\pNet'_i)^{i\in L}\right]\uplus(\pNet'_i)^{i\in J\cap L},S_j^{j\in 
-	%%J\setminus L},
-	%% \symb{SV}_k^{k\in K}\myrangle
-	%% \]
-	\[\pNet\left[\pNet'\right]_{j_0}= \mylangle 
-	\pNet_i^{i\in I}\uplus\{j_0\mapsto \pNet'\},\Sort_j^{j\in J\setminus \{j_0\}},
-	\overline{\symb{SV}}\myrangle
-	\]
-\end{definition}
+transitivity of the bisimulation relation.
 

### 2018-07-25 2016-Weak-FH-Bisim/WeakBisim.tex
intro semantics

@@
 
-\section{Operational Semantics for Open pNets}
+\section{Semantics of Open pNets}
 \label{section:op-semantics}
+
+This section defines the semantics of an open \pNet as a translation into an open automaton. 
+In this translation, the states of the open automata will be obtained from the states of the \pLTS s at the leaves of the composition.
+The predicates on the transition will be obtained both from the predicates on the \pLTS s transitions and from the
+This allows us to derive a bismulation theory for open \pNet s.
+As \pNet s are composition structures, it then makes sense to prove composition lemmas: we prove that the composition of bisimilar pNets are themselves bisimilar.
 

### 2018-07-25 2016-Weak-FH-Bisim/WeakBisim.tex
First draft introduction

@@
 
-\paragraph{Contribution}
+This article provides a theoretical background that allows us to implement such a verification platform.
+We build upon the concept of pNets that allowed us to give a behavioural semantics of distributed components and verify the correctness of distributed applications in the past 15 years.
+pNets  is a
+low level semantic framework for expressing the behaviour of various
+classes of distributed languages, and as a common internal format for
+our tools.  pNets allow the
+specification of parameterised hierarchical labelled
+transition systems:  labelled transition systems with parameters can be
+combined hierarchically.
+
+We develop here a semantics for a model of interacting processes with parameters and holes. 
 The main interest of our symbolic approach is to define a method to
@@
 by any correct instantiation of the holes.
+As a consequence, our model allows us to reason on composition operators as well as on full-size distributed systems.
+The parametric nature of the model and the properties of compositionability of the equivalence relations thus play a major role here and are the main strengths of  our contribution.
+
+\paragraph{Previous Works and Contribution}
+While most of our previous works relied on closed, fully-instantiated semantics~\cite{BBCHM:article2009}, it is only recently that we could design a first version of a  parameterised semantics for pNets with a strong bisimulation equivalence~\cite{henrio:Forte2016}.
+This article builds open this previous parameterised semantics and provide a cleaner version of the semantics with a slightly simplified formalism and extends it to deal with weak bisimulation.
+The slight simplification of the formula allowed us to adopt a much cleaner presentation where the theory for open automata, the algebra used to define the semantics of pNets with holes, can be studied independently from its application to pNets.
+Also, in previous work the study of compositionability was only partial, and in particular the proof that bisimulation is an equivalence is one new contribution of this article and provides a particularly interesting insight on the semantic model we use.
+The new formalism allowed us to extend the work and define weak bisimulation  for open automata, which is entirely new.
+This allows us to define a weak bisimulation equivalence for open pNets with valuable properties of compositionality.
+To summarise, the contribution of this paper are the following
+\begin{itemize}
+\item The definition of open automata: an algebra of parameterised automata with hole with a strong bisimulation equivalence.
+This is an adaptation of~\cite{henrio:Forte2016} with an additional property stating that strong bisimulation equivalence is indeed an equivalence relation.
+\item A semantics for open pNets expressed as translation to open automata. This is an adaptation of~\cite{henrio:Forte2016} with a complete proof that strong bisimulation is compositional.
+\item A theory of weak bisimulation for open automata, and its properties.
+It relies on the definition of weak open transitions that are derived from transitions of the open automaton by concatenating invisible action transitions with one (visible or not) transition.
+The precise definition of the concatenation is also a major contribution of this article.
+\item A resulting weak bisimulation equivalence for open pNets and a simple static condition on synchronisation vectors inside pNets that is sufficient to ensure that weak bisimulation is compositional.
+\item An illustrative example \TODO{TODO}
+\end{itemize}
 
@@
 
-\paragraph{Structure.}
-
-\section{Background and notations}
+\paragraph{Structure}
+This article is organised as follows.
+Section~\ref{sec:notations} provides the definition of pNets and introduces the notations used in this paper.
+Section~\ref{sec:OT} defines open automata, i.e.
+automata with parameters and transitions conditioned by the behaviour of ``holes''; a strong bisimulation equivalence for open automata is also presented in this section.
+Section~\ref{section:op-semantics} gives the semantics of open pNets expressed as weak automata, and states compositional properties on the strong bisimulation for open pNets.
+Finally, Section~\ref{sec:weak} defines a weak bisimulation equivalence on open automata and derives weak bisimilarity for pNets, together with properties on compositionality of weak bisimulaiton for open pNets.
+Finally, Section~\ref{section:conclusion} concludes the paper.
+
+\section{Background and notations}\label{sec:notations}
 This section introduces the notations we will use in this article, and  recalls the definition of pNets~\cite{henrio:Forte2016} with an informal semantics  of the pNet constructs.
@@
 
-\subsection{Open Automata: A model of process composition}
+\section{Open Automata: A model of process composition}
 \label{sec:OT}
@@
 
-\section{Weak bisimulation}
+\section{Weak bisimulation}\label{sec:weak}
 
@@
 computed by hand its full set of transitions. This work would be very
-tedious with pen and paper; we are currently developping a software
+tedious with pen and paper; we are currently developing a software
 tool to this end.

### 2018-07-26 2016-Weak-FH-Bisim/WeakBisim.tex
reorga appendices
Attempt...

--- 2018-07-24 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 % !TEX TS-program = pdflatex
-% !TeX spellcheck = en_GB
 
@@
 \paragraph{Contribution}
-The main interest of our symbolic approach is to define a method to
-prove properties directly on open structures, that will be preserved
-by any correct instantiation of the holes.
 
@@
 
-The informal semantics of \pNet s is as follows.
-\pLTS s behave more or less like  classical automata with conditional branching and variables.
-The actions on the \pLTS s can send or receive values, potentially modifying the value of variables.
-\pNet s are synchronisation entities: a \pNet composes several subnets and  synchronisation vectors define how the subnets interact, where a subnet is either a \pNet or a \pLTS.
-Synchronisation between subnets is defined by synchronisation vectors that express how an action of a subnet can be synchronised with actions of other subnet, and how the resulting synchronised action is visible to the outside of the \pNet.
-Synchronisation vectors also allow to explicitly export an action of a subnet to the next level, or to allow to subnets to synchronise and only exporting a non0observable action (provided such an non-visible action labels exist in the action algebra.
-Finally, a \pNet can leave subnets undefined and instead declare holes with a well-defined signature.
-Holes can then be filled with a subnet.
-This is defined as follows.
-
-\begin{definition}[pNet composition]
-	An open pNet: $\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
-	\overline{\symb{SV}}\myrangle$
- can be (partially) filled by providing  a pNets $\pNet'$ of the
-	right sort to fill one of  its holes.	
-	Suppose $j_0\in J$:
-	%% \[\mylangle \pNet_i^{i\in I},S_j^{j\in J}, \symb{SV}_k^{k\in
-	%%   K}\myrangle\left[(\pNet'_i)^{i\in L}\right]= \mylangle \pNet_i^{i\in
-	%%   I}\left[(\pNet'_i)^{i\in L}\right]\uplus(\pNet'_i)^{i\in J\cap L},S_j^{j\in 
-	%%J\setminus L},
-	%% \symb{SV}_k^{k\in K}\myrangle
-	%% \]
-	\[\pNet\left[\pNet'\right]_{j_0}= \mylangle 
-	\pNet_i^{i\in I}\uplus\{j_0\mapsto \pNet'\},\Sort_j^{j\in J\setminus \{j_0\}},
-	\overline{\symb{SV}}\myrangle
-	\]
-\end{definition}
+\TODO{informal semantics of pnets}
 
@@
 
-\subsection{Open Automata: A model of process composition}
-\label{sec:OT}
-
-The semantics of open \pNet s will be defined  as an open automaton. An open
+\section{Operational Semantics for Open pNets}
+\label{section:op-semantics}
+
+The semantics of open pNets will be defined  as an open automaton. An open
 automaton is an automaton where each transition composes transitions of several LTSs with
@@
 set of state modifications.
-This section defines open automata and a bisimulation theory for them.
-Open automata are not composition structures but they are made of transitions that are dependent of the actions of the holes, and they can reason on variables (potentially with only symbolic values).
 %\TODO{adopt a uniform notation for open transitions, almost each instance has a 
@@
 
-An open automaton is then simply an automaton where each transition is an open transition.
 \begin{definition}[Open automaton]
@@
 \end{definition}
-
-\subsection{Bisimulation for open Automata}
-\label{section:bisimulation}
-
-The equivalence we need is a strong bisimulation between
-pNets having exactly the same Holes with the same sorts, but using a
-flexible matching 
-between open transition, to accommodate comparisons between pNet
-expressions with different architectures.
-
-We define now a bisimulaiton relation adapted to open automata and their parametric nature.
-The relation relates states of the open automaton and states equivalence between the open transitions between the states.
-Its key characteristics are 1) the introduction of predicates in the bisimulation relation: as states may contain variables, relation between states may depend on the value of the variables; 2) the bisimulation property relates elements of the open transitions and take into account predicates over variables, actions of the holes, and state modifications.
- We name it FH-bisimulation,
- as a short cut for the ``Formal Hypotheses'' manipulated in the
- transitions, but also as a reference to the work of De Simone~\cite{deSimone85},
- that pioneered this idea.
-
-Let $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$ be a relation over the set $\mathcal{S}_1$ and 
-$\mathcal{S}_2$ constrained by a predicate
-More precisely, for any pair $(s,t)$, there is a 
-   single
-      $(s,t|\Pred_{s,t})\in\mathcal{R}$  stating that $s$ and $t$ are related 
-      if $\Pred_{s,t}$       is 
-      true, i.e. the states are related when the variables in $s$ and $t$ verify the 
-      predicate $\Pred_{s,t}$.
- FH-bisimulation is defined formally: 
- \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim}
-
-\noindent
-\begin{minipage}{0.69\linewidth} 	Suppose that
-   $A_1 = <\!J,\mathcal{S}_1, s_0,
-   \mathcal{T}_1\!>$ and $A_2 = <\!J,\mathcal{S}_2,t_0, \mathcal{T}_2\!>$
-   are open automata with identical holes of the same sort.
-
- Then 
-$\mathcal{R}$ is an FH-bisimulation iff for any  states
-$s\in\mathcal{S}_1$ and $t\in\mathcal{S}_2$, $(s,t|\Pred_{s,t})\in\mathcal{R}$, we 
-have
-the following:
-\end{minipage}
-\hspace{2mm}
-\begin{minipage}{0.30\linewidth}
-	\includegraphics[width=\linewidth]{XFIG/Bisim}
-%	\TODO{J'ai ajoute les predicats. Il reste a dessiner la ``couverture'' si j'y arrive...}
-\end{minipage}
-
- \begin{itemize}
- \item  For any open transition $OT$ in $\mathcal{T}_1$:
- \begin{mathpar}
-     \openrule
-         {
-           \beta_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
-         {s \OTarrow {\alpha} s'}
-
-\end{mathpar}
- there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
- \begin{mathpar}
-%    \left( fresh \ \overline{\alpha_i}, \overline{b_j}, v_x.\ \
-    \openrule
-         {
-           \beta_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {t \OTarrow {\alpha_x} t_x}
-%         \right)
-\end{mathpar}
- such that  $\forall x, J_1=J_{x}, \exists \Pred_{s',t_x}. (s',t_x|\Pred_{s',t_x})\in 
- \mathcal{R}$; 
- and  \\
- $\Pred_{s,t} \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-   \left( \forall j. \beta_j=\beta_{jx}  \Rightarrow \Pred_{OT_x}
-     \land \alpha\!=\!\alpha_x \land  
-     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
-     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
-     %     \right)$.
-
-%     \TODO{Eric: j'ai ajoute $\exists$ sur les predicats $\Pred_{s',t_x}$, qui n'etaient pas definis...}
-
- \item  and symmetrically any open transition from $t$ in $\mathcal{T}_2$ can be 
-      covered by a set of transitions from $s$ in $\mathcal{T}_1$.
- \end{itemize}
-
-% \TODO{Eric: il reste des petits bugs genre $s^{2'}_x$ plutot que
-%   $s^{2}_x$}
-
-%Where $\symb{Subst}(\Pred,\Post)$ is the parallel substitution of all
-%assigned variables.
-
-% \TODO{do we want formulas for this?}
- \end{definition}
-Classically, $\Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}$
-applies in parallel the  
-substitutions $\Post_{OT}$ and $\Post_{OT_x}$ (parallelism is crucial
-inside each $\Post$ set but not between  $\Post_{OT}$ and
-$\Post_{OT_x}$ that are independent), applying the assignments of the involved rules.
-We can prove that such a bisimulation si an equivalence relation:
-
-\begin{theorem}[FH-Bisimulation is an equivalence]\label{thm-equiv} Suppose $\mathcal{R}$ 
-is an FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
-reflexive, symmetric and transitive.
-
-\end{theorem}
-
-\medskip
-
-If we assume that everything is finite (states and transitions in the
-open automata, and the predicates in $\mathcal{R}$, then it is easy to
-prove that it is decidable whether a relation is a 
-FH-bisimulation, provided the logic of the predicates is decidable (see \cite{henrio:Forte2016}).
-
-\begin{theorem}[Decidability of FH-bisimulation]
-Let $A_1$ and $A_2$ be finite open automata
-and $\mathcal{R}$ a relation over their states $\mathcal{S}_1$ and
-$\mathcal{S}_2$ constrained by a finite set of predicates. Assume that
-the predicates inclusion is decidable over  
-the action algebra $\mathcal{A}_P$. Then it is decidable whether the relation 
-$\mathcal{R}$ is a FH-bisimulation.
-
-\end{theorem}
-
-\section{Operational Semantics for Open pNets}
-\label{section:op-semantics}
 
@@
 \subsection{Computing and using open automata}
-\TODO{REMOVE?}
 In this section we present a simple algorithm to construct the open
@@
 
-\subsection{Bisimulation for open \pNet s and Composability}
-\label{section:bisimulation-PN}
-As  our symbolic operational semantics provides an open automaton, we can apply the notion of
-	strong (symbolic) bisimulation on automata to open \pNet s:
-\begin{definition}[FH-bisimulation for open \pNet s]\label{def:bisim-pnets}
+\section{Bisimulation}
+\label{section:bisimulation}
+
+	Now we use our symbolic operational semantics to define a notion of
+	strong (symbolic) bisimulation. Moreover this equivalence is decidable whenever we 
+	have some
+	decision procedure on the predicates of the action algebra.
+
+%% , that we prove compatible with the
+%% composition of open pNets. \TODO{do we really know this ?}
+
+The equivalence we need is a strong bisimulation between
+pNets having exactly the same Holes with the same sorts, but using a
+flexible matching 
+between open transition, to accommodate comparisons between pNet
+expressions with different architectures.
+ We name it FH-bisimulation,
+ as a short cut for the ``Formal Hypotheses'' manipulated in the
+ transitions, but also as a reference to the work of De Simone~\cite{deSimone85},
+ that pioneered this idea.
+
+Let $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$ be a relation over the set $\mathcal{S}_1$ and 
+$\mathcal{S}_2$ constrained by a predicate
+More precisely, for any pair $(s,t)$, there is a 
+   single
+      $(s,t|\Pred_{s,t})\in\mathcal{R}$  stating that $s$ and $t$ are related 
+      if $\Pred_{s,t}$ 
+      is 
+      true, i.e. the states are related when the variables in $s$ and $t$ verify the 
+      predicate $\Pred_{s,t}$.
+ FH-bisimulation is defined formally: 
+ \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim}
+
+\noindent
+\begin{minipage}{0.69\linewidth} 	Suppose that
+   $A_1 = <\!J,\mathcal{S}_1, s_0,
+   \mathcal{T}_1\!>$ and $A_2 = <\!J,\mathcal{S}_2,t_0, \mathcal{T}_2\!>$
+   are open automata with identical holes of the same sort.
+
+ Then 
+$\mathcal{R}$ is an FH-bisimulation iff for any  states
+$s\in\mathcal{S}_1$ and $t\in\mathcal{S}_2$, $(s,t|\Pred_{s,t})\in\mathcal{R}$, we 
+have
+the following:
+\end{minipage}
+\hspace{2mm}
+\begin{minipage}{0.30\linewidth}
+	\includegraphics[width=\linewidth]{XFIG/Bisim}
+%	\TODO{J'ai ajoute les predicats. Il reste a dessiner la ``couverture'' si j'y arrive...}
+\end{minipage}
+
+ \begin{itemize}
+ \item  For any open transition $OT$ in $\mathcal{T}_1$:
+ \begin{mathpar}
+     \openrule
+         {
+           \beta_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
+         {s \OTarrow {\alpha} s'}
+
+\end{mathpar}
+ there exist open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
+ \begin{mathpar}
+%    \left( fresh \ \overline{\alpha_i}, \overline{b_j}, v_x.\ \
+    \openrule
+         {
+           \beta_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {t \OTarrow {\alpha_x} t_x}
+%         \right)
+\end{mathpar}
+ such that  $\forall x, J_1=J_{x}, \exists \Pred_{s',t_x}. (s',t_x|\Pred_{s',t_x})\in 
+ \mathcal{R}$; 
+ and  \\
+ $\Pred_{s,t} \land \Pred_{OT}\\
+\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
+   \left( \forall j. \beta_j=\beta_{jx}  \Rightarrow \Pred_{OT_x}
+     \land \alpha\!=\!\alpha_x \land  
+     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
+     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
+     %     \right)$.
+
+%     \TODO{Eric: j'ai ajoute $\exists$ sur les predicats $\Pred_{s',t_x}$, qui n'etaient pas definis...}
+
+ \item  and symmetrically any open transition from $t$ in $\mathcal{T}_2$ can be 
+      covered by a set of transitions from $s$ in $\mathcal{T}_1$.
+ \end{itemize}
+
+% \TODO{Eric: il reste des petits bugs genre $s^{2'}_x$ plutot que
+%   $s^{2}_x$}
+
+%Where $\symb{Subst}(\Pred,\Post)$ is the parallel substitution of all
+%assigned variables.
 Two pNets are FH-bisimilar if there exist a relation between their associated 
@@
 the predicate associated to the relation between the initial states is true.
+% \TODO{do we want formulas for this?}
  \end{definition}
-We can now prove that \pNet\ composition  preserves
+Classically, $\Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}$
+applies in parallel the  
+substitutions $\Post_{OT}$ and $\Post_{OT_x}$ (parallelism is crucial
+inside each $\Post$ set but not between  $\Post_{OT}$ and
+$\Post_{OT_x}$ that are independent), applying the assignments of the involved rules.
+
+\medskip
+If we assume that everything is finite (states and transitions in the
+open automata, and the predicates in $\mathcal{R}$, then it is easy to
+prove that it is decidable whether a relation is a 
+FH-bisimulation, provided the logic of the predicates is decidable (see \cite{henrio:Forte2016}).
+
+\begin{theorem}[Decidability of FH-bisimulation]
+Let $A_1$ and $A_2$ be finite open automata
+and $\mathcal{R}$ a relation over their states $\mathcal{S}_1$ and
+$\mathcal{S}_2$ constrained by a finite set of predicates. Assume that
+the predicates inclusion is decidable over  
+the action algebra $\mathcal{A}_P$. Then it is decidable whether the relation 
+$\mathcal{R}$ is a FH-bisimulation.
+
+\end{theorem}
+
+\section{Composability}
+
+The main interest of our symbolic approach is to define a method to
+prove properties directly on open structures, that will be preserved
+by any correct instantiation of the holes. In this section we define a
+composition operator for open pNets, and we prove that it preserves
 FH-bisimulation. More precisely, one can define two preservation
-properties, namely 1) when one hole of a \pNet\ is filled by two bisimilar other (open) pNets; and 2) when the same hole in two bisimilar pNets are
+properties, namely 1) when one hole of a pNet is filled by two bisimilar other (open) pNets; and 2) when the same hole in two bisimilar pNets are
 filled by the same pNet, in other words, composing a pNet with two
 bisimilar contexts. The general case will be obtained by
-transitivity of the bisimulation relation.
+transitivity of the bisimulation relation. We concentrate here on the
+second property, that is the most interesting.
+
+\begin{theorem}[FH-Bisimulation is an equivalence]\label{thm-equiv} Suppose $\mathcal{R}$ 
+is an FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
+reflexive, symmetric and transitive.
+
+\end{theorem}
+
+\begin{definition}[pNet composition]
+	An open pNet: $\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
+	\overline{\symb{SV}}\myrangle$
+ can be (partially) filled by providing  a pNets $\pNet'$ of the
+	right sort to fill one of  its holes.	
+	Suppose $j_0\in J$:
+	%% \[\mylangle \pNet_i^{i\in I},S_j^{j\in J}, \symb{SV}_k^{k\in
+	%%   K}\myrangle\left[(\pNet'_i)^{i\in L}\right]= \mylangle \pNet_i^{i\in
+	%%   I}\left[(\pNet'_i)^{i\in L}\right]\uplus(\pNet'_i)^{i\in J\cap L},S_j^{j\in 
+	%%J\setminus L},
+	%% \symb{SV}_k^{k\in K}\myrangle
+	%% \]
+	\[\pNet\left[\pNet'\right]_{j_0}= \mylangle 
+	\pNet_i^{i\in I}\uplus\{j_0\mapsto \pNet'\},\Sort_j^{j\in J\setminus \{j_0\}},
+	\overline{\symb{SV}}\myrangle
+	\]
+\end{definition}
 
@@
 \begin{mathpar}
-  \mprset {vskip=.5ex}
-\inferrule {\openrule
+%\mprset {vskip=.5ex}
+%\inferrule 
+\forall i \in [0\ldots n].\openrule
     {
        \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
-         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}
-\qquad
+         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
+\quad
 \openrule
          {
-           \overline{\beta^2_i},\Pred^2_i,\Post^2_i  }
-         {s^2_i \OTarrow {\alpha} s^2_{i+1}} \in \mathcal{T}
-\qquad
-\openrule
+           \overline{\beta^2},\Pred^2,\Post^2 }
+         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
+\quad \wedge\\
+\forall i \in [0\ldots m].\openrule
          {
@@
          {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
+\end{mathpar}
+such that\\
+\begin{mathpar} 
+s=s^1_0 \wedge s^1_n=s^2_0 \wedge s'^2 = s^3_0 \wedge s^3_m=s'
+\\\\
+\overline{\gamma}=\biguplus_{i=0}^n \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^m \vis{\overline{\beta^3_i}}
 \\
-s=s^1_i \wedge s^1_n=s^2_0 \wedge s^2_n = s^3_0 \wedge s^3_n=s'
-\\\\
-\overline{\gamma}=\biguplus_{i=0}^n \vis{\overline{\beta^1_i}} \dotcup  \biguplus_{i=0}^n \vis{\overline{\beta^2_i}} \dotcup \biguplus_{i=0}^n \vis{\overline{\beta^3_i}}
+\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred^2\subst{\Post_1}\land (\bigwedge_{i=0}^m\Pred^3_i\subst{\Post^2})\subst{\Post^1_i}
+
+\end{mathpar}
+
+\begin{mathpar}
+\Longleftrightarrow  \left \{ \begin{array}{l} 
+\alpha = \tau \wedge  \vis{\overline{\beta^2}}=\emptyset \wedge \Pred^2 =\symb{True} \wedge \Post^2 =\symb{Id(s)}\\
 \\
-\Pred=\bigwedge_{i}^n\Pred^1_i\land\bigwedge_{i}^n\Pred^2_i\subst{\Post_1}\land (\bigwedge_{i}^n\Pred^3_i\subst{\Post^2_i})\subst{\Post^1_i}
-}
+\bigvee \\
+\\
 {
@@
 		\Pred,
-				({x^3_k\gets (e^3_k\subst {\Post^2_i})\subst{\Post^1_i}})^{k\in K} } 
+				({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K} } 
          {s \OTWeakarrow {\alpha} s'} \in\WT
 }
+\end{array}
+\right.
 \end{mathpar}
+
 \end{lemma}
 
-\begin{proof} 
-We proceed by induction on the depth of the derivation tree with with we  build  a weak transition (introduced in Definition \ref{def:buildweakOT}).
-The base cases  are:
-\begin{itemize}
-\item $n=0$, then we have by rule (1)
+\begin{proof} ($\Rightarrow$) We proceed by induction by induction the number of transitions with which we  build  a weak transition (introduced in Definition \ref{def:buildweakOT}).
+The base case  is if $n=0$ and $m=0$ then 
 \begin{mathpar}
+ % \mprset {vskip=.5ex}
+%\inferrule{
  \openrule
          {
-           \emptyset,\symb{True},\symb{Id}(s)}
-         {s \OTWeakarrow {\tau} s}
-         \in \WT
-
+           \overline{\beta},\Pred,\Post}
+         {s \OTarrow {\alpha} s'} \in \mathcal{T}
+%}
+%}
 \end{mathpar} 
-\item $n=1$, then by rule (2) we have:
+and by rule (2) we have
  \begin{mathpar}
@@
 \end{mathpar} 
-\end{itemize}
-For the inductive step, first we have by induction hypothesis that
+For the inductive step, first we have by induction hypothesis that the formula is valid for some length $l$ such that $l=n+m+1$, we have 
+\TODO{I will complete}
+
+on other hand by rule (2) we have
+\begin{mathpar}
+ % \mprset {vskip=.5ex}
+\inferrule{
+ \openrule
+         {
+           \overline{\beta},\Pred,\Post}
+         {s \OTarrow {\tau} s'} \in \mathcal{T}
+}
+{ \openrule
+         {
+           \vis{\overline{\beta}}\!,\Pred,\Post
+				 } {s \OTWeakarrow {\tau} s'} \in \WT
+}
+\end{mathpar}
+
+\noindent ($\Leftarrow$) We proceed also by induction on the depth of the inference of 
 \begin{mathpar}
@@
 \end{mathpar}
+First, using rule (1) we can directly conclude \\
+
+Second by using rule (2),  
+\begin{mathpar}
+{ \openrule
+         {
+          \overline{\gamma} \!,\Pred,\Post
+				 } {s \OTWeakarrow {\alpha} s'} \in \WT
+}
+\end{mathpar}
+implies that 
+\begin{mathpar}
+\openrule
+         {
+           \overline{\beta},\Pred,\Post}
+         {s \OTarrow {\alpha} s'} \in \mathcal{T}
+\end{mathpar}
+such that $\overline{\gamma} = \vis{\overline{\beta}}$.\\
+Finally by using rule (3) we have
+\begin{mathpar}
+\inferrule{
+\openrule
+         {
+           \overline{\gamma_1},\Pred_1,\Post_1   }
+         {s \OTWeakarrow {\tau} s_1} \in\! \WT
+\quad
+\openrule
+         {
+           \overline{\gamma_2},\Pred_2,\Post_2  }
+         {s_1 \OTWeakarrow {\alpha} s_2} \in\! \WT
+\quad
+\openrule
+         {
+           \overline{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
+         {s_2 \OTWeakarrow {\tau} s'} \in\!\WT
+\\
+\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
+}{}
+\end{mathpar}
+and by induction hypothesis this means that we have first,
+\begin{mathpar}
+%\inferrule{
+\openrule
+         {
+           \overline{\gamma_1},\Pred_1,\Post_1   }
+         {s \OTWeakarrow {\tau} s_1} \in\! \WT
+
+\end{mathpar}
+
+implies
+
+\begin{mathpar}
+\forall i \in [0\ldots n_1].\openrule
+    {
+       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
+         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}         
+\end{mathpar}
+
+such that\\
+\begin{mathpar} 
+s=s^1_0 \wedge s^1_{n_1}=s_1 \quad
+\overline{\gamma_1}=\biguplus_{i=0}^{n_1} \vis{\overline{\beta^1_i}} 
+\quad
+\Pred_1=\bigwedge_{i=0}^{n_1}\Pred^1_i\quad \Post_1= \biguplus_{i=0}^{n_1} \Post_i^1
+\end{mathpar}
+
+Secondly,
+\begin{mathpar}
+\openrule
+         {
+           \overline{\gamma_2},\Pred_2,\Post_2  }
+         {s_1 \OTWeakarrow {\alpha} s_2} \in\! \WT
+
+\end{mathpar}
+implies
+\begin{mathpar}
+\forall i \in [0\ldots n_2].\openrule
+    {
+       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
+         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
+\quad
+\openrule
+         {
+           \overline{\beta^2},\Pred^2,\Post^2 }
+         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
+\quad \wedge\\
+\forall i \in [0\ldots m_2].\openrule
+         {
+           \overline{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
+         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
+\end{mathpar}
+such that\\
+\begin{mathpar} 
+s_1=s^1_0 \wedge s^1_n=s^2_0 \wedge s'^2 = s^3_0 \wedge s^3_{m_2}=s_2
+\\\\
+\overline{\gamma}=\biguplus_{i=0}^{n_2} \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^{m_2} \vis{\overline{\beta^3_i}}
+\\
+\Pred=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred^2\subst{\Post_1}\land (\bigwedge_{i=0}^{m_2}\Pred^3_i\subst{\Post^2})\subst{\Post^1_i}
+
+\end{mathpar}
+Finally,
+\begin{mathpar}
+%\inferrule{
+\openrule
+         {
+           \overline{\gamma_3},\Pred_3,\Post_3   }
+         {s_2 \OTWeakarrow {\tau} s'} \in\! \WT
+
+\end{mathpar}
+
+implies
+
+\begin{mathpar}
+\forall i \in [0\ldots m_1].\openrule
+    {
+       \overline{\beta^3_i},\Pred^3_i,\Post^3_i   }
+         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}         
+\end{mathpar}
+
+such that\\
+\begin{mathpar} 
+s_2=s^3_0 \wedge s^1_{m_1}=s' \quad
+\overline{\gamma_3}=\biguplus_{i=0}^{m_1} \vis{\overline{\beta^3_i}} 
+\quad
+\Pred_3=\bigwedge_{i=0}^{m_1}\Pred^3_i\quad \Post_3= \biguplus_{i=0}^{m_1} \Post_i^3
+\end{mathpar}
+
 \end{proof}
+
+------------------------------------------------------
+
 Using this lemma, it is straightforward to see that....  

### 2018-07-26 2016-Weak-FH-Bisim/WeakBisim.tex

--- 2018-07-25 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
-       \section{Proofs of basic properties on pNets}
-       \subsection{Equivalence relation (Theorem~\ref{thm-equiv})}
+       \section{Bisimulation is an equivalence: Proof of Theorem~\ref{thm-equiv}}
         \emph{Suppose $\mathcal{R}$ 
@@
 
+       \section{Proofs of properties on pNets}
 \subsection{Composition Lemmas}       

### 2018-08-29 2016-Weak-FH-Bisim/WeakBisim.tex

@@
 
-\TODO{should we use iff/implies or LeftRightArrow/Rightarrow}
+Global and questions:
+\begin{itemize}
+\item \TODO{should we use iff/implies or LeftRightArrow/Rightarrow}
+
+\item \TODO{uniformiser pNet \pNet pNet s \pNet s (dans le texte et les formules!)}
+
+\item \TODO{proposition Ludo \& Rabea: \pNet -> P,Q dans les formules pour que ce soit moins long}
+\end{itemize}
+Ludo:
 \begin{itemize}
@@
 \paragraph{Previous Works and Contribution}
-While most of our previous works relied on closed, fully-instantiated semantics~\cite{BBCHM:article2009}, it is only recently that we could design a first version of a  parameterised semantics for pNets with a strong bisimulation equivalence~\cite{henrio:Forte2016}.
+While most of our previous works relied on closed, fully-instantiated semantics~\cite{BBCHM:article2009,AmeurBoulifa2017,HKM-FASE16}, it is only recently that we could design a first version of a  parameterised semantics for pNets with a strong bisimulation equivalence~\cite{henrio:Forte2016}.
 This article builds open this previous parameterised semantics and provide a cleaner version of the semantics with a slightly simplified formalism and extends it to deal with weak bisimulation.
@@
 \paragraph{Related works}
+
+\TODO{TODO ... or rather a dedicated section}
 
@@
 \end{definition}
+
+pNets are composition entities equipped with a rich synchronisation mechanism: synchronisation vectors allows the expression of synchronisation between any number of entities and at the same time the passing of data between processes.
+Their strongest feature is that the data emitted by processes can be used can be used inside the synchronisation vector to do addressing: it is easy to synchronise a process indexed by $n$ with the action $a(v,n)$ of another process.
+This is very convenient to model systems and encode futures or message routing.
+pNets have been used to model GCM distributed component systems, illustrating the expressiveness of the model~\cite{AmeurBoulifa2017}.
+These works show that pNets are convenient to express the behaviour of the system in a compositional way, which is crucial for the definition of the semantics, especially when dealing with a hierarchical component system like GCM.
+Unfortunately, the semantics of pNets and the existing tools at this point were only able to deal with a closed system completely instantiated: pNets could be used as composition operator in the definition of the semantics, which was sufficient to perform finite-state model checking on a closed system, but there was no theory for the use of pNets as operators and no tool for proving properties on open system.
+The semmantics of closed pNets~\cite{AmeurBoulifa2017}, defined as an instantiation of labelled transition systems, is not necessary to understand this article but can be useful to  understand the semantics of pNets in a simpler and more operational setting.
+The theory of pNets as operators able to fully take into account open systems is given in the rest of this article.
 
@@
 
+Though the definition is simple, the fact that transitions are complex structures relating events must not be underestimated in order to understand the rest of the article.
+The first element of theory for open automata, i.e.
+the definition of a strong bisimulation, is given below.
+
 \subsection{Bisimulation for open Automata}
@@
 reflexive, symmetric and transitive.
-
 \end{theorem}
+
+The proof of this theorem can be found in Appendix~\ref{thm-equiv-proof}.
+The only non-trivial part of the proof is the proof of transitivity.
+It relies on the following elements.
+First,  the transitive composition of two relations with predicate is defined; this is not exactly standard as it necessitates to define the right predicate for the transitive composition and producing a single predicate to relate any two states.
+Then the fact that one open transition is simulated by a family of open transitions leads to a doubly indexed family of simulating open transition; this needs particular care, also because of the use of renaming (\Post) when proving that the predicates satisfy the definition (property on $\Pred_{s,t} \land \Pred_{OT}$ in the definition).
+
+\TODO{have a look at the end of the sec}
 
@@
 
-       \section{Bisimulation is an equivalence: Proof of Theorem~\ref{thm-equiv}}
+       \section{Bisimulation is an equivalence: Proof of Theorem~\ref{thm-equiv}}\label{thm-equiv-proof}
         \emph{Suppose $\mathcal{R}$ 

### 2018-09-03 2018-ModelCheckingPNets/checking.tex
The source file

%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\let\origvec\vec
\documentclass[runningheads,a4paper]{llncs}

%******Figure and Table Package
\usepackage{color}
\usepackage{amsfonts}
%\usepackage{ulem}    % underline/strikethrough/wave lines
\usepackage{graphicx}  % figures
\usepackage{tabularx}
\usepackage{subfigure}
\usepackage{graphicx}
\usepackage{caption}
%\usepackage{subcaption}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{shapes,shadows,calc}
\usepgflibrary{arrows}

\newcommand{\A}{\mathcal{A}}
\newcommand{\K}{\mathcal{K}}
\newcommand{\M}{\mathcal{M}}
\newcommand{\T}{\mathcal{T}}

\tikzset{
	sshadow/.style={opacity=.25, shadow xshift=0.05, shadow yshift=-0.06},
}

%-----#1 size, #2 angle, #3 aspect, #4 label next to the diamond
%-----#5 name of the node, #6 coordinate, #7 label
\def\schemel[#1,#2,#3,#4,#5,#6]#7{ %
	\node[draw, diamond, shape aspect=#3, rotate=#2, minimum size=#1, %
	bottom color=green!55, top color=green!25, color=green!65!black, %
	drop shadow={sshadow,color=green!60!black}, #4] (#5) at #6
	{\textcolor{green!40}{bla}}; %
	\node at #6 {#7};%
}

\def\schemer[#1,#2,#3,#4,#5,#6]#7{ %
	\node[draw, diamond, shape aspect=#3, rotate=#2, minimum size=#1, %
	bottom color=green!65, top color=green!30, color=green!60!black, %
	drop shadow={sshadow,color=green!65!black}, #4] (#5) at #6
	{\textcolor{green!53}{bla}}; %
	\node at #6 {#7}; %
}

%-----TBoxes
%-----#1 height, #2 width, #3 anchor for the label, #4 name of the node, #5
%-----coordinate, #6 label
\def\tboxl[#1,#2,#3,#4,#5]#6{%
	\node[draw, drop shadow={opacity=.35}, minimum height=#1, minimum width=#2, %
	inner color=blue!45, outer color=blue!55, color=blue!40!black] (#4) at #5 {}; %
	\node[anchor=#3,inner sep=2pt] at (#4.#3) {#6};%
}

\def\tboxr[#1,#2,#3,#4,#5]#6{%
	\node[draw, drop shadow={opacity=.35}, minimum height=#1, minimum width=#2, %
	inner color=blue!35, outer color=blue!45, color=blue!50!black] (#4) at #5 {}; %
	\node[anchor=#3,inner sep=2pt] at (#4.#3) {#6}; %
}

%-----#1 name of the node, #2 coordinate, #3 label
\def\entity[#1,#2]#3;{
	\node[draw,drop shadow={opacity=.4,shadow xshift=0.04, shadow
		yshift=-0.04},color=blue!30!black,fill=white,rounded corners=3] (#1) at #2 {#3};
}

%-----#1 from node, #2 to node, #3 specification of a node (label), #4
%-----dashed, or other parameters for draw
\def\isaedge[#1,#2,#3,#4];{ 
	\draw[-triangle 60,color=black!20!black,#4,fill=white] (#1) -- #3
	(#2);  
}

%-----ABoxes
%-----#1 height, #2 width, #3 aspect, #4 name of the node, #5
%-----coordinate, #6 label
\def\aboxl[#1,#2,#3,#4,#5]#6{%
	\node[draw, cylinder, alias=cyl, shape border rotate=90, aspect=#3, %
	minimum height=#1, minimum width=#2, outer sep=-0.5\pgflinewidth, %
	color=orange!40!black, left color=orange!70, right color=orange!80, middle
	color=white] (#4) at #5 {};%
	\node at #5 {#6};%
	\fill [orange!30] let \p1 = ($(cyl.before top)!0.5!(cyl.after top)$), \p2 =
	(cyl.top), \p3 = (cyl.before top), \n1={veclen(\x3-\x1,\y3-\y1)},
	\n2={veclen(\x2-\x1,\y2-\y1)} in (\p1) ellipse (\n1 and \n2); }

\def\aboxr[#1,#2,#3,#4,#5]#6{%
	\node[draw, cylinder, alias=cyl, shape border rotate=90, aspect=#3, %
	minimum height=#1, minimum width=#2, outer sep=-0.5\pgflinewidth, %
	color=orange!50!black, left color=orange!50, right color=orange!60, middle
	color=white] (#4) at #5 {};%
	\node at #5 {#6};%
	\fill [orange!20] let \p1 = ($(cyl.before top)!0.5!(cyl.after top)$), \p2 =
	(cyl.top), \p3 = (cyl.before top), \n1={veclen(\x3-\x1,\y3-\y1)},
	\n2={veclen(\x2-\x1,\y2-\y1)} in (\p1) ellipse (\n1 and \n2); }

%-----#1 height, #2 width, #3 name of the node, #4
%-----coordinate, #5 label
\def\kbbox[#1,#2,#3,#4,#5]#6{
	\draw[dashed] node[draw,color=gray!50,minimum
	height=#1,minimum width=#2] (#4) at #5 {}; 
	\node[anchor=#3,inner sep=2pt] at (#4.#3)  {#6};
}

%-----#1 from node, #2 to node, #3 specification of a node (label), #4
%-----dashed, or other parameters for draw
\def\soledge[#1,#2,#3,#4];{
	\draw[dashed,-latex,#4] (#1) -- #3 (#2);
}

%**********Math package

\let\springervec\vec
\let\vec\origvec
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{latexsym}
\setcounter{tocdepth}{3}
\usepackage{graphicx}

%---Algorithm
\renewcommand{\thechapter}{\Roman{chapter}}
\renewcommand{\thesection}{\arabic{section}}

\usepackage[chapter]{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}

\renewcommand{\thealgorithm}{\arabic{chapter}.\arabic{algorithm}}

%----Graph
\usepackage{tikz,mathpazo}  % This package is used to draw the figure
\usetikzlibrary{shapes.geometric, arrows}
\usetikzlibrary{positioning,shapes.geometric}

\usepackage{palatino}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}
\usepackage{xcolor}
\usetikzlibrary{shapes,arrows,chains}

\usepackage{url}

\urldef{\mailstu}\path|{tengfei.li}@stu.ecnu.edu.cn| 
\urldef{\mailecnu}\path|{jliu, hysun}@sei.ecnu.edu.cn|      
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{Model Checking for Open Concurrent Systems}

% a short form should be given in case it is too long for the running head
\titlerunning{Lecture Notes in Computer Science: Authors' Instructions}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Tengfei Li
%\thanks{Corresponding author}%
\and Eric Madelaine \and *
}
%
\authorrunning{Lecture Notes in Computer Science: Authors' Instructions}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address unless you accept that it will be published

\institute{
%\mailstu\\
%\mailecnu\\
}

%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%

\toctitle{Lecture Notes in Computer Science}
\tocauthor{Authors' Instructions}
\maketitle

\begin{abstract}

The verification of concurrent systems, especially concurrent systems with data, have been researched for many years. However, the composition of concurrent systems have not been solved well. The major problem is ...

\keywords{ pM$\mu$\quad $pMG $\quad pLTS }
\end{abstract}

\section{Introduction}
% no \IEEEPARstart

\section{Describing pLTS}

\subsection{pLTS}

In a pLTS, each state is composed of a set of $\mathit{state\ variables}$, and a transition is defined between two states. A triple with $\mathit{parameterised\ action}, \mathit{guard}$ and $\mathit{assignment}$ consists of the labelling function of the transition.

\subsubsection{Definition of pLTS}
We define pLTS as a triple: $pLTS\triangleq\ll S, s_{0}, \rightarrow \gg$ where:
\begin{itemize}
	\item $S$ is a set of states, and $s_{0}\in S$ is the initial state.
	\item $\rightarrow \subseteq S\times L\times S$ is the transition relation, with $L$ the set of labels of form $<\alpha, e_{b}, (x_{j} := e_{j})^{(j\in J)}>$, where $\alpha\in A_{V}$ is a parameterised action, $e_{b}\in B_{V}$ is a guard, and expression $E_{P}\cup A_{P}$ are assigned to $x_{j}$. If $s\xrightarrow{<\alpha, e_{b}, (x_{j}:=e_{j})^{j\in J}>}s' \in \rightarrow$, then $vars(e_{b})\subseteq vars(s)\cup vars(\alpha)$, and $\forall j\in J. vars(e_{j})\subseteq vars(s)\wedge x_{j}\in vars(s')$.
\end{itemize}

\begin{figure}
	\centering
	\begin{tikzpicture}[->, shorten >=2pt, >=stealth, node distance=3cm,
	noname/.style={ellipse, minimum width=5em, minimum height=3em,draw}]
	\node[noname] (1)                                             {$s_{0}$};
	\node[noname] (2) [right=of 1]                                {$s_{1}$};

	\path 	(1) edge [bend left]                  node[above] {$[true],\langle start?M\rangle,\{t:=M\}$} (2)
	(2) edge [bend left]                  node[below] {$[t=0], \langle timeout\rangle$} (1)
	(2) edge 			               node[above] {$\langle resume\rangle$} (1);
	\path[->] (2) edge [in=-10,out=20,loop] coordinate[pos=0.52] (midp) node[right] {$[t>0], \langle tick\rangle, \{t:=t-1\}$} (2);

	\end{tikzpicture}
	\caption{The pLTS of the Timer component}
\end{figure}

\subsubsection{Semantics of pLTS}

\subsection{Property Language}

A major difference of pLTS from other concurrent systems is the parameterised action. Basic MCL\cite{radu2008mcl} extends action in modal $\mu$-calculus with data variables, so it suits for describing the property of open concurrent systems. We define a subset of basic MCL, named parameterised modal $\mu$-calculus (pM$\mu$), to describe the properties of pLTS. Tab.~\ref{mcl} shows the syntax of pM$\mu$.

\begin{table}
	%	\multirow{2}{*}{Algorithme}
	\setlength\tabcolsep{18pt}% default value is 6pt 
	\centering 
	\caption{Syntax of the pM$\mu$} 
	\label{mcl}
	\begin{tabular}{>{\bfseries}c| c } 
		\hline 		
	Action formula 	&     $\alpha ::= \{c(arg_{1}, ..., arg_{n})\mid arg_{i}=?x\ |\ !e\ |\ \tau \}$                  \\
	& $|\ \neg\alpha \ |\ \alpha_{1}\vee\alpha_{2}\ |\ \alpha_{1}\wedge\alpha_{2}$   \\ 	\hline

	State formula 	&  $\varphi ::= p \ |\ \neg\varphi \ |\ \varphi_{1}\wedge\varphi_{2}\ |\ \varphi_{1}\vee\varphi_{2} \ |\ [\alpha]\varphi \ |\ \langle\alpha\rangle\varphi$ \\ 
	& $\exists x_{i}\varphi\ |\ \forall x_{i}\varphi\ |\ \mu X(e_{i}/x_{i})\varphi\ |\ \nu X(e_{i}/x_{i})\varphi$	\\ \hline 
	\end{tabular}

\end{table}

 where, $c$ is an action name expressing the communication port. $arg_{i}$ is a list of arguments, and each $arg_{i}$ is either a send expression $!e$, or a receive variable $?x$. $p$ is an atomic proposition.  
  {\color{red}{[To do Tengfei: Must complete the explaination ]}}.

We employ the case study from timer component\cite{mavridou2016architectrue}. A liveness property defines that good thing finally happens. In this case study, intuitively the timer finally returns to the initial state after some execution steps. The property can be expressed by pM$\mu$:

\begin{equation}\label{formula1}
	\langle start?M\rangle\mu X(M/t)(\langle timeout\rangle true \vee \langle tick\rangle X(t-1/t))
\end{equation}

At first, we can do $\langle start?M\rangle$ and then enters a loop.

where, 
\begin{itemize}
\item either it can do a $timeout$ and then we are done and the result is true.
\item or we can do a $tick$ and then we continue the loop, decreasingly, the value t 
\end{itemize}

\subsection{pMG}

Modal graph is present by Lin\cite{lin2001modal}. We consider a variant of modal graph, parameterised modal graph (pMG), as the graphical version of pM$\mu$. A pMG is a directed graph $\langle N, E, L_{N}, n_{0}\rangle$, where
\begin{itemize}
	\item $N$ is a set of nodes.
	\item $E \subset N\times N$ is the set of edges.
	\item $L_{N} = (L_{V}, L_{O}, L_{D})$ associates each node $n\in N$ a set of variables $L_{V}(n)$, an operator $L_{O}(n)\in\{\wedge, \vee, \forall x, \exists x,  {\color{red}{\alpha(args)}}, \theta\}\cup  {\color{red}{ModOp}} \cup BExp$, and a depth $L_{D}(n)$ which is a natural number.
	\item $n_{0} \in N$ is the root of pMG.
\end{itemize}

Fig.~\ref{architectrue} presents the architecture of model checking. After we describe the property of a pLTS with pM$\mu$, we transfer the pM$\mu$ formula to pMG. After that, we will {\color{red}{verify the pLTS model with the pMG by the algorithm}}.

{\color{red}{[To do Tengfei: Be more precise]}}

\begin{figure}
    \centering\includegraphics[width=5.5in]{figures/architectrue.jpeg} 
    \caption{Architecture of symbolic model checking}
    \label{architectrue}
\end{figure}

\subsection{Transformation from pM$\mu$ to pMG}

The transformation rules can be seen in Lin's paper~\cite{lin2001modal}. The rules take a pM$\mu$ formula as the input and generate a pMG.

In the case study, the liveness property is present as Formula~\ref{formula1}. The alternation depth is 1, because there is only one $\mu$ operator. The corresponding modal graph is shown as follows:

\begin{figure}
	\begin{tikzpicture}[->, shorten >=2pt, >=stealth, node distance=2cm,
	noname/.style={ellipse, minimum width=2.5em, minimum height=1.5em, draw}]
	\node[noname] (1)                                            				 	{$t_{1}$};
	\node[noname] (2) [right=of 1]                               				 	{$t_{2}$};
	\node[noname] (3) [right=of 2]                              				 	{$t_{3}$};
	\node[noname] (4) [node distance=0.5cm and 2cm, above right=of 3]    {$t_{4}$};
	\node[noname] (5) [right=of 4]                                					{$t_{5}$};
	\node[noname] (6) [node distance=0.5cm and 2cm, below right=of 3]     {$t_{6}$};

	\path 	(1) edge                   	node[above] {} (2)
	(2) edge                   	node[above] {} (3)
	(3) edge 			node[above] {} (4)
	(3) edge 			node[above] {} (6)
	(6) edge[bend left]    node[below] {} (3)
	(4) edge    		node[below] {} (5);
	\end{tikzpicture}
	\caption{The associated pMG}
\end{figure}
where:
\begin{itemize}
	\item $L_{N}(t_{1}) = (\{\}, \langle start?M\rangle, 1)$
	\item $L_{N}(t_{2}) = (\{t\}, t := M, 1)$
	\item $L_{N}(t_{3}) = (\{t\}, \vee, 1)$
	\item $L_{N}(t_{4}) = (\{t\}, \langle timeout\rangle, 1)$
	\item $L_{N}(t_{5}) = (\{\}, true, 1)$
	\item $L_{N}(t_{6}) = (\{t\}, \langle tick\rangle, 1)$
\end{itemize}

\section{The algorithm}

\subsection{Background}

 In \cite{lin1996stga}, Lin presents a symbolic transition graph with assignment (STGA) to model concurrent processes. In a STGA, a node is associated with a set of variables. and the edge between nodes is labelled by guard, assignment and action with a tuple $(b, \bar{x}:=\bar{e}, \alpha)$. The first-order $\mu$-calculus is employed as the property language. In order to check the graph, the first-order $\mu$-calculus is transferred to a graphical version through the proposed rules, and then we check {\color{red}{STGA and the modal graph}} by the algorithm.

 \subsubsection{Parameterised action}
From the perspective of syntax, pLTS is similar to STGA. The difference between pLTS and STGA is the $\mathit{action}$. An action in pLTS is a parameterised action $c(args)$. From the syntax of pM$\mu$, we define the parameters in the action as $args$, and $args$ can be one of $!e$, $?x$ and $null$ or the composition of them. While an action in STGA is either a silent action $\tau$, an input action $c?x$, or an output action $c!e$, where $c\in Chan$.

The difference in parameterised action results in the difference in modality of the algorithm. Based on similarity, we check the pLTS through modifying the algorithm, especially in the modality.

\subsubsection{Alternation-free pM$\mu$}

A formula is said to be alternation-free, when the alternation depth is one, without mutually recursive greatest and least fixed-point operators. A formula expressed with pM$\mu$ is alternation-free. But the formula with first-order $\mu$-calculus have to deal with alternation depth.{\color{red}{[To do Tengfei: definition of alternation depth]}}

 {\color{red}{The order of action and conditional expression???}}
Another difference is the order of action and conditional expression. In pLTS, the order is $<\alpha, e_{b}, (x_{j}:=e_{j})^{j\in J}>$,  and $vars(e_{b})\subseteq vars(s)\cup vars(\alpha)$, and $\forall j\in J. vars(e_{j})\subseteq vars(s)\wedge x_{j}\in vars(s')$.

While it is $< b, \bar{x}=\bar{e}, \alpha>$ in STGA.

\subsection{Abstract data domain}

In a pLTS, the parameterised action $start(?M)$ includes a parameter in it, and whether the parameter is a variable or a constant is unknown at the abstract level. Abstract values are associated with parameters instead of concrete values \cite{cousot1976static}. We use a symbolic interpretation on parameters $M$.

{\color{red}{
To to Eric:
In order to construct the abstract data domains, we divide the value of $Max$ to variable and constant. If Max is a variable, Max can express the interval on integer. The change of the value is controlled by a self-decreasing operator. Also, we need another integer 0 as the minimal boundary. If Max is a constant, i.e. Max is the maximal boundary and 0 is the minimal boundary. So we need another variable $pos$ as the interval between Max and 0. Fig.~\ref{side:a} and Fig.~\ref{side:b} are two interpretations on the data domain of the variables. Fig.~\ref{side:a} shows an interpretation that includes two constant (Max, 0), a variable (pos) and an operator (-) on the integer. While Fig.~\ref{side:b} specifies that $Max$ is a variable.
}}

\begin{figure}[htbp]

	\begin{tikzpicture}[->, shorten >=2pt, >=stealth, node distance=1.5cm,
	noname/.style={ellipse, minimum width=2.5em, minimum height=1.5em,draw}]
	\node[noname] (1)                                             {$Max$};
	\node[noname] (2) [node distance=0.5cm and 2cm, above right=of 1]                                {$0$};
	\node[noname] (3) [node distance=0.5cm and 2cm, below right=of 1]                                {$pos$};

	\path 	(1) edge                   	node[above] {$-$} (2)
	(1) edge                   	node[above] {$-$} (3)
	(3) edge                   node[right] {$-$} (2);
	\path[->] (3) edge [in=-10,out=20,loop] coordinate[pos=0.52] (midp) node[right] {$-$} (3);
	\end{tikzpicture}
	\caption{Interpretation on $Max$}   \label{side:a}

\end{figure}

\subsection{The algorithm for checking pLTS}

\subsubsection{Processing parameterised action}
We change the algorithm to make it suitable for checking pLTS. From the syntax of pM$\mu$, we define the parameters in the action as $args$, and $args$ can be one of $!e$, $?x$ and $null$ or the composition of them. In the modification version, we change the modality $[c!e], \langle c!e\rangle$, $[c?x], \langle c?x\rangle$ to $[c]$, $\langle c\rangle$, $[c(args)], \langle c(args)\rangle$.
It was shown as follows:

$[c]\Rightarrow$ $checkAnd(\{ (p_{i}, (n', \rho))\,|\, p \xrightarrow{c} p_{i}, n\rightarrow n' \})$

$\langle c\rangle\Rightarrow$ 
	 $checkOr(\{ (p_{i}, (n',\rho))\,|, p \xrightarrow{c} p_{i}, n \rightarrow n'\})$

$[c(?x, !e)]\Rightarrow$
	$ checkAnd(\{ (p_{i}[v/y], (n',\rho\{x \rightarrow v\}))\,|\,  n \rightarrow n', p \xrightarrow{c(?y, !\rho(e)) } p_{i},v\in Val\})$

{$\langle c(?x, !e)\rangle\Rightarrow$}
	 $ checkOr(\{ (p_{i}[v/y], (n', \rho\{x \rightarrow v\}))\,|\,  n \rightarrow n', p \xrightarrow{c(?y, !\rho(e))} p_{i},v\in Val\})$

The full algorithm can be seen in the appendix.

\subsubsection{Processing alternation-free pM$\mu$}
The formula in pM$\mu$ is alternation-free, so the alternation depth is 1 in each node of pMG. In the model checking graph, we don't need to use recursion, and the function $restore(D, b)$ in the algorithm is useless for checking pLTS.

{\color{red}{[The principle of model checking]}}
Given a pLTS model $M$ and a pMG formula $f$, the algorithm checks whether the model satisfies the formula $M\models f$. Each state is made up with a couple $\{s\rho, n\rho'\}$, where $s$ is a state in pLTS, and $n$ a node of pMG. A transition of the model checking graph is from $\{s\rho, n\rho_{0}\}$ to $\{s'\rho', n'\rho_{0}'\}$.

\subsection{The execution result}

After running the algorithm in the appendix, the model checking graph is shown in Fig.~\ref{checkinggraph}:

\begin{figure}
	\begin{tikzpicture}[->, shorten >=2pt, >=stealth, node distance=2cm,
	noname/.style={ellipse, minimum width=3em, minimum height=1.5em, draw}]
	\node[noname] (1)                                             {$S_{0}$};
	\node[noname] (10) [node distance=0.5cm and 2cm, above right=of 1]                                {$S_{10}$};
	\node[noname] (11) [node distance=0.5cm and 2cm, below right=of 1]                                {$S_{11}$};
	\node[noname] (20) [node distance=0.5cm and 2cm, above right=of 10]                                {$S_{20}$};
	\node[noname] (30) [node distance=0.5cm and 2cm, above right=of 20]                                {$S_{30}$};
	\node[noname] (31) [node distance=0.5cm and 2cm, below right=of 20]                                {$S_{31}$};
	\node[noname] (40) [right=of 30]                                {$S_{40}$};

	\node[noname] (21) [node distance=0.5cm and 2cm, below right=of 11]                                {$S_{21}$};
	\node[noname] (32) [node distance=0.5cm and 2cm, above right=of 21]                                {$S_{32}$};
	\node[noname] (33) [node distance=0.5cm and 2cm, below right=of 21]                                {$S_{33}$};
	\node[noname] (41) [right=of 32]                                {$S_{41}$};

	\path 	(1) edge                   	node[above] {$\langle start?M\rangle,1$} (10)
	(1) edge                   	node[above] {$\langle start?M\rangle,1$} (11)
	(10) edge                   node[above] {${\mu},1$} (20)
	(20) edge                 	node[above] {$\vee,1$} (30)
	(20) edge                 	node[above] {$\vee,1$} (31)
	(31) edge [bend left] 			node[below] {$\langle true\rangle,1$} (20)
	(30) edge               	node[above] {$\langle timeout\rangle,1$} (40)

	(11) edge                   node[above] {${\mu},1$} (21)
	(21) edge                 	node[above] {$\vee,1$} (32)
	(21) edge                 	node[above] {$\vee,1$} (33)
	(33) edge [bend left] 			node[below] {$\langle true\rangle,1$} (21)
	(32) edge               	node[above] {$\langle timeout\rangle,1$} (41);

	\end{tikzpicture}
	\caption{Model checking Graph}
	\label{checkinggraph}
\end{figure}
where:
\begin{itemize}
	\item $S_{0}  = (\{s_{0},s_{[\rho=\emptyset]}\}, \{n_{1}, \rho_{0}'=\emptyset\}\;|\;s.\sigma = false)$
	\item $S_{10} = (\{s_{1},s_{[t\leftarrow 0]}\}, \{n_{2}, \rho_{0}'(M\leftarrow 0)\}\;|\;s.\sigma = false)$
	\item $S_{20} = (\{s_{1},s_{[t\leftarrow pos]}\}, \{n_{3}, \rho_{0}'(t\leftarrow n_{2})\}\;|\;s.\sigma = false)$
	\item $S_{30} = (\{s_{1},s_{[t\leftarrow 0]}\}, \{n_{4}, \rho_{0}'(t\leftarrow 0)\}\;|\;s.\sigma = false)$
	\item $S_{31} = (\{s_{1},s_{[t\leftarrow 0]}\}, \{n_{5}, \rho_{0}'(t\leftarrow 0)\}\;|\;s.\sigma = false)$
	\item $S_{40} = (\{s_{0},s_{\rho[true]}\}, \{n_{6}, \rho_{0}'(true)\}\;|\;s.\sigma = true)$

	\item $S_{11} = (\{s_{1},s_{[t\leftarrow pos]}\}, \{n_{2}, \rho_{0}'(M\leftarrow pos)\}\;|\;s.\sigma = false)$
	\item $S_{21} = (\{s_{1},s_{[t\leftarrow pos]}\}, \{n_{3}, \rho_{0}'(t\leftarrow n_{2})\}\;|\;s.\sigma = false)$
	\item $S_{32} = (\{s_{1},s_{[t\leftarrow 0]}\}, \{n_{4}, \rho_{0}'(t\leftarrow 0)\}\;|\;s.\sigma = false)$
	\item $S_{33} = (\{s_{1},s_{\rho[t\leftarrow t-1]}\}, \{n_{5}, \rho_{0}'(t\leftarrow t-1)\}\;|\;s.\sigma = false)$
	\item $S_{41} = (\{s_{0},s_{\rho[true]}\}, \{n_{6}, \rho_{0}'(true)\}\;|\;s.\sigma = true)$
	\item $n_{2}'=\mu X(pos/t)(\langle timeout\rangle true \vee \langle true\rangle X(pos-1))$
	\item $n_{3}=\langle timeout\rangle true \vee\langle true\rangle\mu X(pos)(\langle timeout\rangle true \vee \langle true\rangle X(pos-1))$
\end{itemize}

In the initial state, there is no variable for the pLTS. After the action $start(?M)$ triggers the transition from $s_{0}$ to $s_{1}$, the value of the variable $t$ will be changed to $Max$. In the transition, the action expression of the operator in the edge of pMG will trigger the occurrence of transitions in pLTS. The change of value in $s$ depends on the semantics of pLTS. In the state $s_{1}$, the system will check whether the guard $t>0$ satisfies. If yes, the action $tick$ will lead to the occurrence of loop transition. Or, the system will enter another transition back to the initial state $s_{0}$. {\color{red}{[After executing the model checking graph, it will finally return to state $S_{40}$ or state $S_{41}$. Both of them are true.}}

\section{Checking open automata}

\subsection{The difference between pLTS and open automata}

\subsection{}

\subsection{}

\section{Related work and Conclusion}

\section*{Appendix}

\algnewcommand\algorithmicswitch{\textbf{switch}}
\algnewcommand\algorithmiccase{\textbf{case}}
\algnewcommand\algorithmicassert{\texttt{assert}}
\algnewcommand\Assert[1]{\State \algorithmicassert(#1)}%
% New "environments"
\algdef{SE}[SWITCH]{Switch}{EndSwitch}[1]{\algorithmicswitch\ #1\ \algorithmicdo}{\algorithmicend\ \algorithmicswitch}%
\algdef{SE}[CASE]{Case}{EndCase}[1]{\algorithmiccase\ #1}{\algorithmicend\ \algorithmiccase}%
\algtext*{EndSwitch}%
\algtext*{EndCase}%

\begin{algorithm} 
	\begin{algorithmic}[1]
		\State stack[0 ... (k-l)]
		\State pushStack(s) = push s onto stack[s.depth]
		\State top() = return the top element of the first non-empty stack with the deepest depth
		\State pop() = remove from the stack the element returned by the last call to top 
		\State $s=\{s.depth, s.status, s.\sigma, s.D, s.instack\}$
		\State modelCheck(s) = \{ s.status := VISITED($s.\sigma)$; push(s);
		\While{stack is non-empty}
		\State close(top()); \Return s.status; \}
		\EndWhile

	\end{algorithmic} 
	\caption{modelCheck(s)}
	\label{alg:algorithm1}
\end{algorithm}

\begin{algorithm} 
	\begin{algorithmic}[1]

		\State close(s as ($p, n\rho'$)) =
		\If{n is root}
		\State $p = m\rho; \rho = \emptyset; \rho' = \emptyset$  
		\EndIf
		\State let checkAnd(W) =
		\State let ($B_{i}, D_{i}$) = check($s_{i}$) 
		\For {each $s_{i} \in W$}
		\If {there is some $B_{i}$ = DEFERRED}
		\Return(DEFERRED)
		\ElsIf {there is some $B_{i}$ = VALUE(false)} 
		\State add s to $D_{i}$; \Return(VALUE(false))
		\Else 
		\State add s to each $D_{i}$; \Return(VALUE(true))
		\EndIf
		\EndFor
		\State let checkOr(W) =
		\State let ($B_{i}, D_{i}$) = check($s_{i}$) 
		\For {each $s_{i} \in W$}
		\If {every $B_{i}$ = DEFERRED}
		\Return(DEFERRED)
		\ElsIf{there is some $B_{i}$ = VALUE(true)} 
		\State add s to $D_{i}$; \Return(VALUE(true))
		\Else 
		\State add s to each $D_{i}$; \Return(VALUE(false))
		\EndIf
		\EndFor

		\State  let $B$ be 
		\Switch{$L_{O}(n)$} 
		\Case{$be$}
		\Return $\rho(be)$
		\EndCase
		\Case{x:=e}
		\Return $checkAnd(\{ (p, (n', \rho\{x\rightarrow \rho(e)\}))\, |\, n \rightarrow n' \})$
		\EndCase
		\Case{$\wedge$} 
		\Return $checkAnd(\{ (p, (n_{i}, \rho))\, n\rightarrow n_{i}\}) $
		\EndCase
		\Case{$\vee$} 
		\Return $checkOr(\{ (p, (n_{i}, \rho))\, n\rightarrow n_{i} \})$
		\EndCase
		\Case{[c]} 
		\Return $checkAnd(\{ (p_{i}, (n', \rho))\,|\, p \xrightarrow{c} p_{i}, n\rightarrow n' \})$
		\EndCase
		\Case{$\langle c\rangle$} 
		\Return $checkOr(\{ (p_{i}, (n',\rho))\,|, p \xrightarrow{c} p_{i}, n \rightarrow n'\})$
		\EndCase
		\Case{[c(?x, !e)]}
		\Return $ checkAnd(\{ (p_{i}[v/y], (n',\rho\{x \rightarrow v\}))\,|\,  n \rightarrow n', p \xrightarrow{c(?y, !\rho(e)) } p_{i},v\in Val\})$
		\EndCase
		\Case{$\langle c(?x, !e)\rangle$}
		\Return $ checkOr(\{ (p_{i}[v/y], (n', \rho\{x \rightarrow v\}))\,|\,  n \rightarrow n', p \xrightarrow{c(?y, !\rho(e))} p_{i},v\in Val\})$
		\EndCase
		\Case{$\forall x$}
		\Return $  checkAnd(\{ (p, (n',\rho\{x \rightarrow v\}))\,|\, n \rightarrow n', v \in Val\})$
		\EndCase
		\Case{$\exists x$}
		\Return $ checkOr(\{ (p, (n',\rho\{x \rightarrow v\}))\,|\,  n \rightarrow n', v\in Val\})$
		\EndCase
		\EndSwitch

		\If{B=VALUE(b)}
		\State pop(); 
		\If{s.status = VISITED($b'$) and $b'\neq b$}
		\State s.status = VISITED($b$); 
		\EndIf
		\EndIf
	\end{algorithmic} 
	\caption{$close(s)$}
	\label{alg:algorithm1}
\end{algorithm}

\begin{algorithm} 
	\begin{algorithmic}[1]
		\State check(s) =
		\Switch{$s.status$}
		\Case{FRESH} 
		\State s.status := VISITED($s.\sigma$); push($s$); \Return (DEFERRED, $s.D$)
		\EndCase
		\Case{VISITED($b$)} 
		\Return (VALUE($b$), $s.D$)
		\EndCase
		\EndSwitch

	\end{algorithmic} 
	\caption{check(s)}
	\label{alg:algorithm2}
\end{algorithm}

\begin{thebibliography}{4}

	\bibitem{radu2008mcl}Mateescu, Radu, and Damien Thivolle. "A model checking language for concurrent value-passing systems." International Symposium on Formal Methods. Springer, Berlin, Heidelberg, 2008.

	\bibitem{mavridou2016architectrue} Mavridou, Anastasia, et al. "Architecture-based design: A satellite on-board software case study." International Workshop on Formal Aspects of Component Software. Springer, Cham, 2016.
	\bibitem{lin2001modal} Lin, Huimin. "Model checking value-passing processes." apsec. IEEE, 2001.

	\bibitem{lin1996stga} Lin, Huimin. "Symbolic transition graph with assignment." International Conference on Concurrency Theory. Springer, Berlin, Heidelberg, 1996.
	\bibitem{cousot1976static}Cousot, Patrick, and Radhia Cousot. "Static determination of dynamic properties of programs." Proceedings of the 2nd International Symposium on Programming, Paris, France. Dunod, 1976.

\end{thebibliography}

\end{document}

### 2018-09-05 2018-ModelCheckingPNets/checking.tex
add pNet packages

@@
 
+%----- pNet macros package
+\usepackage{epsfig,enumitem}
+\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
+\newcommand{\NOTE}[1]{\textcolor{blue}{\textbf{[NOTE:#1]}}}
+\newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
+\definecolor{darkgreen}{rgb}{0.1, 0.5, 0.1}
+\newcommand{\coloncolon}{{:\hspace{-.2ex}:}}
+\makeatletter
+\newcommand{\raisemath}[1]{\mathpalette{\raisem@th{#1}}}
+\newcommand{\raisem@th}[3]{\raisebox{#1}{$#2#3$}}
+\makeatother
+
+\usepackage{macrospNets}
+
 \usepackage{url}
@@
 % no \IEEEPARstart
+
+\section{Use-case: The BIP Failure-Timer architecture}
+\TODO{Describe here the full Failure-Timer architecture, as taken from the Avocs paper, including an informal presentation of the original BIP system, its full translation into a pNet system (pLTSs and pNet nodes), and the generated Open Automaton}
+\NOTE{All figures are already available from the Avocs paper sources.}
 
@@
 $p$ is an atomic proposition.
-  {\color{red}{[To do Tengfei: Must complete the explaination ]}}.
+  \TODO{Tengfei: Must complete the explaination}.
 
@@
 
-{\color{red}{[To do Tengfei: Be more precise]}}
+\TODO{Tengfei: Be more precise}
 

### 2018-09-06 2018-ModelCheckingPNets/checking.tex
More explanation

@@
 \usepgflibrary{arrows}
-
-\newcommand{\A}{\mathcal{A}}
-\newcommand{\K}{\mathcal{K}}
-\newcommand{\M}{\mathcal{M}}
-\newcommand{\T}{\mathcal{T}}
-
-\tikzset{
-	sshadow/.style={opacity=.25, shadow xshift=0.05, shadow yshift=-0.06},
-}
-
-%-----#1 size, #2 angle, #3 aspect, #4 label next to the diamond
-%-----#5 name of the node, #6 coordinate, #7 label
-\def\schemel[#1,#2,#3,#4,#5,#6]#7{ %
-	\node[draw, diamond, shape aspect=#3, rotate=#2, minimum size=#1, %
-	bottom color=green!55, top color=green!25, color=green!65!black, %
-	drop shadow={sshadow,color=green!60!black}, #4] (#5) at #6
-	{\textcolor{green!40}{bla}}; %
-	\node at #6 {#7};%
-}
-
-\def\schemer[#1,#2,#3,#4,#5,#6]#7{ %
-	\node[draw, diamond, shape aspect=#3, rotate=#2, minimum size=#1, %
-	bottom color=green!65, top color=green!30, color=green!60!black, %
-	drop shadow={sshadow,color=green!65!black}, #4] (#5) at #6
-	{\textcolor{green!53}{bla}}; %
-	\node at #6 {#7}; %
-}
-
-%-----TBoxes
-%-----#1 height, #2 width, #3 anchor for the label, #4 name of the node, #5
-%-----coordinate, #6 label
-\def\tboxl[#1,#2,#3,#4,#5]#6{%
-	\node[draw, drop shadow={opacity=.35}, minimum height=#1, minimum width=#2, %
-	inner color=blue!45, outer color=blue!55, color=blue!40!black] (#4) at #5 {}; %
-	\node[anchor=#3,inner sep=2pt] at (#4.#3) {#6};%
-}
-
-\def\tboxr[#1,#2,#3,#4,#5]#6{%
-	\node[draw, drop shadow={opacity=.35}, minimum height=#1, minimum width=#2, %
-	inner color=blue!35, outer color=blue!45, color=blue!50!black] (#4) at #5 {}; %
-	\node[anchor=#3,inner sep=2pt] at (#4.#3) {#6}; %
-}
-
-%-----#1 name of the node, #2 coordinate, #3 label
-\def\entity[#1,#2]#3;{
-	\node[draw,drop shadow={opacity=.4,shadow xshift=0.04, shadow
-		yshift=-0.04},color=blue!30!black,fill=white,rounded corners=3] (#1) at #2 {#3};
-}
-
-%-----#1 from node, #2 to node, #3 specification of a node (label), #4
-%-----dashed, or other parameters for draw
-\def\isaedge[#1,#2,#3,#4];{ 
-	\draw[-triangle 60,color=black!20!black,#4,fill=white] (#1) -- #3
-	(#2);  
-}
-
-%-----ABoxes
-%-----#1 height, #2 width, #3 aspect, #4 name of the node, #5
-%-----coordinate, #6 label
-\def\aboxl[#1,#2,#3,#4,#5]#6{%
-	\node[draw, cylinder, alias=cyl, shape border rotate=90, aspect=#3, %
-	minimum height=#1, minimum width=#2, outer sep=-0.5\pgflinewidth, %
-	color=orange!40!black, left color=orange!70, right color=orange!80, middle
-	color=white] (#4) at #5 {};%
-	\node at #5 {#6};%
-	\fill [orange!30] let \p1 = ($(cyl.before top)!0.5!(cyl.after top)$), \p2 =
-	(cyl.top), \p3 = (cyl.before top), \n1={veclen(\x3-\x1,\y3-\y1)},
-	\n2={veclen(\x2-\x1,\y2-\y1)} in (\p1) ellipse (\n1 and \n2); }
-
-\def\aboxr[#1,#2,#3,#4,#5]#6{%
-	\node[draw, cylinder, alias=cyl, shape border rotate=90, aspect=#3, %
-	minimum height=#1, minimum width=#2, outer sep=-0.5\pgflinewidth, %
-	color=orange!50!black, left color=orange!50, right color=orange!60, middle
-	color=white] (#4) at #5 {};%
-	\node at #5 {#6};%
-	\fill [orange!20] let \p1 = ($(cyl.before top)!0.5!(cyl.after top)$), \p2 =
-	(cyl.top), \p3 = (cyl.before top), \n1={veclen(\x3-\x1,\y3-\y1)},
-	\n2={veclen(\x2-\x1,\y2-\y1)} in (\p1) ellipse (\n1 and \n2); }
-
-%-----#1 height, #2 width, #3 name of the node, #4
-%-----coordinate, #5 label
-\def\kbbox[#1,#2,#3,#4,#5]#6{
-	\draw[dashed] node[draw,color=gray!50,minimum
-	height=#1,minimum width=#2] (#4) at #5 {}; 
-	\node[anchor=#3,inner sep=2pt] at (#4.#3)  {#6};
-}
-
-%-----#1 from node, #2 to node, #3 specification of a node (label), #4
-%-----dashed, or other parameters for draw
-\def\soledge[#1,#2,#3,#4];{
-	\draw[dashed,-latex,#4] (#1) -- #3 (#2);
-}
 
@@
 
-\urldef{\mailstu}\path|{tengfei.li}@stu.ecnu.edu.cn| 
-\urldef{\mailecnu}\path|{jliu, hysun}@sei.ecnu.edu.cn|      
+\urldef{\mailtengfei}\path|{tengfeili2018}@gmail.com| 
+\urldef{\mailinria}\path|{eric.madelaine}@inria.fr|      
 \newcommand{\keywords}[1]{\par\addvspace\baselineskip
@@
 \institute{
-%\mailstu\\
-%\mailecnu\\
+%\mailtengfei\\
+%\mailinria\\
 }
@@
 		\hline 		
-	Action formula 	&     $\alpha ::= \{c(arg_{1}, ..., arg_{n})\mid arg_{i}=?x\ |\ !e\ |\ \tau \}$                  \\
+	Action formula 	&     $\alpha ::= \{\{c(arg_{1}, ..., arg_{n}), \tau\}\mid arg_{i}=?x\ |\ !e\  \}$                  \\
 	& $|\ \neg\alpha \ |\ \alpha_{1}\vee\alpha_{2}\ |\ \alpha_{1}\wedge\alpha_{2}$   \\ 	\hline
 
-	State formula 	&  $\varphi ::= p \ |\ \neg\varphi \ |\ \varphi_{1}\wedge\varphi_{2}\ |\ \varphi_{1}\vee\varphi_{2} \ |\ [\alpha]\varphi \ |\ \langle\alpha\rangle\varphi$ \\ 
+	State formula 	&  $\varphi ::= p \mid X \mid \neg\varphi \mid \varphi_{1}\wedge\varphi_{2}\ |\ \varphi_{1}\vee\varphi_{2} \ |\ [\alpha]\varphi \ |\ \langle\alpha\rangle\varphi$ \\ 
 	& $\exists x_{i}\varphi\ |\ \forall x_{i}\varphi\ |\ \mu X(e_{i}/x_{i})\varphi\ |\ \nu X(e_{i}/x_{i})\varphi$	\\ \hline 
 	\end{tabular} 
-
 \end{table}
@@
 $arg_{i}$ is a list of arguments, and each $arg_{i}$ is either a send expression $!e$, or a receive variable $?x$.
-$p$ is an atomic proposition.
-  \TODO{Tengfei: Must complete the explaination}.
+An action $\alpha$ is a parameterised action $c(arg_{i})$ or a silent action $\tau$.
+$p$ is an atomic proposition and $X$ is a set of variables.
+$\neg$, $\vee$ and $\wedge$ are respectively negation, disjunction and conjunction operator on action formula and state formula.
+$[\alpha]\varphi$ expresses "whenever an action $\alpha$ happens, we will do $\varphi$", and $\langle\alpha\rangle$ expresses "an action $\alpha$ takes effective, we will do $\varphi$".
+$x_{i}\in X$ is a free variable bound in state formula $\varphi$.
+$\mu$ and $\nu$ are respectively the minimum fixed point and the maximum fixed point.\TODO{Tengfei: Must more explaination}
 
@@
 In this case study, intuitively the timer finally returns to the initial state after some execution steps.
-The property can be expressed by pM$\mu$:
+The property can be expressed by pM$\mu$ formula:
 
@@
 
-At first, we can do $\langle start?M\rangle$ and then enters a loop.
-
-where, 
-\begin{itemize}
-\item either it can do a $timeout$ and then we are done and the result is true.
-\item or we can do a $tick$ and then we continue the loop, decreasingly, the value t 
-\end{itemize}
+At first, we can do $\langle start?M\rangle$ and then it enters a loop.
+After that, either we can do a $timeout$, and then it is done and the result is true.
+Or we can do a $tick$ and then we continue the loop with decrementing the value $t$ by one.
 
@@
 We consider a variant of modal graph, parameterised modal graph (pMG), as the graphical version of pM$\mu$.
+We define a collection of modal operators as $ModOp = \{[\alpha], \langle\alpha\rangle\}$.
 A pMG is a directed graph $\langle N, E, L_{N}, n_{0}\rangle$, where
@@
 	\item $N$ is a set of nodes.
-	\item $E \subset N\times N$ is the set of edges.
-	\item $L_{N} = (L_{V}, L_{O}, L_{D})$ associates each node $n\in N$ a set of variables $L_{V}(n)$, an operator $L_{O}(n)\in\{\wedge, \vee, \forall x, \exists x,  {\color{red}{\alpha(args)}}, \theta\}\cup  {\color{red}{ModOp}} \cup BExp$, and a depth $L_{D}(n)$ which is a natural number.
-	\item $n_{0} \in N$ is the root of pMG.
+	\item $E \subseteq N\times N$ is the set of edges.
+	\item $L_{N} = (L_{V}, L_{O}, L_{D})$ associates each node $n\in N$ a set of variables $L_{V}(n)$, an operator $L_{O}(n)\in\{\wedge, \vee, \forall x, \exists x, \theta\}\cup ModOp \cup BExp$, and a depth $L_{D}(n)$ which is a natural number.
+	\item $n_{0} \in N$ is the root of a pMG.
 \end{itemize}
-
-Fig.~\ref{architectrue} presents the architecture of model checking.
-After we describe the property of a pLTS with pM$\mu$, we transfer the pM$\mu$ formula to pMG.
-After that, we will {\color{red}{verify the pLTS model with the pMG by the algorithm}}.
-
-\TODO{Tengfei: Be more precise}
-
-\begin{figure}
-    \centering\includegraphics[width=5.5in]{figures/architectrue.jpeg} 
-    \caption{Architecture of symbolic model checking}
-    \label{architectrue}
-\end{figure}
 
@@
 
-The transformation rules can be seen in Lin's paper~\cite{lin2001modal}. The rules take a pM$\mu$ formula as the input and generate a pMG.
+ Given a pM$\mu$ formula $F$ and a pMG, we define a node as a subformula $\phi$ of $F$.
+The edge between two nodes will be the transition from a subformula to another subformula.
+The transformation rules can be seen in Lin's paper~\cite{lin2001modal}.
+The rules take a pM$\mu$ formula as the input and generate a pMG.
 
@@
 \begin{figure}
-	\begin{tikzpicture}[->, shorten >=2pt, >=stealth, node distance=2cm,
-	noname/.style={ellipse, minimum width=2.5em, minimum height=1.5em, draw}]
+\centering
+	\begin{tikzpicture}[->, shorten >=2pt, >=stealth, node distance=1.2cm,
+	noname/.style={ellipse, minimum width=1.5em, minimum height=1.5em, draw}]
 	\node[noname] (1)                                            				 	{$t_{1}$};
@@
 
-\section{The algorithm}
+Fig.~\ref{architectrue} presents the architecture of model checking.
+The core of the figure is the model checking algorithm, which will be present in Sec.~\ref{algorithm}.
+The algorithm takes a pLTS model and a pM$\mu$ formula as the input.
+First, we describe the property of a concurrent system with pM$\mu$ formula and transfer the pM$\mu$ formula to a pMG.
+And then, the pMG will be verified with the pLTS model by the algorithm.
+After that, the result will return true or false.
+
+\TODO{Tengfei: Be more precise}
+
+\begin{figure}
+    \centering\includegraphics[width=5.5in]{figures/architectrue.jpeg} 
+    \caption{Architecture of symbolic model checking}
+    \label{architectrue}
+\end{figure}
+
+\section{The algorithm}\label{algorithm}
 
@@
 The first-order $\mu$-calculus is employed as the property language.
-In order to check the graph, the first-order $\mu$-calculus is transferred to a graphical version through the proposed rules, and then we check {\color{red}{STGA and the modal graph}} by the algorithm.
+In order to check the graph, the first-order $\mu$-calculus is transferred to a graphical version through the proposed rules, and then STGA is checked by the modal graph by the algorithm.
 
@@
 
-The difference in parameterised action results in the difference in modality of the algorithm. Based on similarity, we check the pLTS through modifying the algorithm, especially in the modality.
+The difference in parameterised action results in the difference in modality of the algorithm. Based on similarity, we have to change the modality and check the pLTS through the modified algorithm.
 
-\subsubsection{Alternation-free pM$\mu$}
+The notation of alternation depth is given by Emerson and Lei in~\cite{emerson1986alternation} as follows:
+
+\textbf{Definition of Alternation Depth}
+Given a pM$\mu$ formula $\Phi$, $\Phi_{i}$ is a subformula of $\Phi$ and $\Gamma_{i}$ is a containing fixed point subformula of $\Phi$.
+The alternation depth $ad(\Phi)$ of $\Phi$ is defined as follows:
+
+\begin{itemize}
+\item[-] $ad(A) = ad(X) = 0$, for any atomic proposition $A$ and variable $X$.
+\item[-] $ad(\Phi_{1}\wedge\Phi_{2}) = ad(\Phi_{1}\vee\Phi_{2}) = max\{ ad(\Phi_{1}), ad(\Phi_{2})\}$.
+\item[-] $ad([\alpha]\Phi) = ad(\langle\alpha\rangle\Phi) = ad(\Phi)$.
+\item[-] Let $\sigma\in\{\mu,\nu\}$, and $\bar{\sigma}$ be the dual of $\sigma$. Then
+	\begin{center}
+	$ad(\sigma X.\Phi) = max\{1, ad(\Phi), 1+ad(\bar{\sigma} X_{1}.\Phi_{1}), ... , 1+ ad(\bar{\sigma} X_{n}.\Phi_{n})\}$
+	\end{center} 
+	where $\bar{\sigma} X_{1}.\Phi_{1}, ... , \bar{\sigma} X_{n}.\Phi_{n}$ are subpromula of $\Phi$.
+\end{itemize}
 
@@
 A formula expressed with pM$\mu$ is alternation-free.
-But the formula with first-order $\mu$-calculus have to deal with alternation depth.{\color{red}{[To do Tengfei: definition of alternation depth]}}
+But the formula with first-order $\mu$-calculus have to deal with alternation depth.\TODO{definition of alternation depth]}
+\NOTE{A formula expressed with pM$\mu$ is alternation-free. !!!NO}
 
@@
 
-{\color{red}{
-To to Eric:
+\TODO{
 In order to construct the abstract data domains, we divide the value of $Max$ to variable and constant.
@@
 While Fig.~\ref{side:b} specifies that $Max$ is a variable.
-}}
+}
 
@@
 From the syntax of pM$\mu$, we define the parameters in the action as $args$, and $args$ can be one of $!e$, $?x$ and $null$ or the composition of them.
-In the modification version, we change the modality $[c!e], \langle c!e\rangle$, $[c?x], \langle c?x\rangle$ to $[c]$, $\langle c\rangle$, $[c(args)], \langle c(args)\rangle$.
+In the modification version, we change the modality from $[c!e], \langle c!e\rangle$, $[c?x], \langle c?x\rangle$ to $[c]$, $\langle c\rangle$, $[c(args)], \langle c(args)\rangle$.
 It was shown as follows:
@@
 
-{\color{red}{[The principle of model checking]}}
-Given a pLTS model $M$ and a pMG formula $f$, the algorithm checks whether the model satisfies the formula $M\models f$.
-Each state is made up with a couple $\{s\rho, n\rho'\}$, where $s$ is a state in pLTS, and $n$ a node of pMG.
+\TODO{The principle of model checking}
+Given a pLTS model $M$ and a pM$\mu$ $f$, the algorithm checks whether the model satisfies the formula $M\models f$.
+First, the pM$\mu$ is transferred to a pMG.
+As for the compositional model checking graph of pMG and pLTS, each state is made up with a couple $\{s\rho, n\rho'\}$, where $s$ is a state in pLTS, and $n$ a node of pMG.
 A transition of the model checking graph is from $\{s\rho, n\rho_{0}\}$ to $\{s'\rho', n'\rho_{0}'\}$.
+The label of the transition is the same as that of pLTS, and the label of the state is the same as that of the node in pMG.
 
@@
 Or, the system will enter another transition back to the initial state $s_{0}$.
-{\color{red}{[After executing the model checking graph, it will finally return to state $S_{40}$ or state $S_{41}$.
-Both of them are true.}}
+\TODO{After executing the model checking graph, it will finally return to state $S_{40}$ or state $S_{41}$.
+Both of them are true.}
 
@@
 	\bibitem{lin1996stga} Lin, Huimin. "Symbolic transition graph with assignment." International Conference on Concurrency Theory. Springer, Berlin, Heidelberg, 1996.
+	\bibitem{emerson1986alternation}Emerson, E. Allen and Chin-Laung Lei. ?Efficient Model Checking in Fragments of the Propositional Mu-Calculus (Extended Abstract).? LICS (1986).
 	\bibitem{cousot1976static}Cousot, Patrick, and Radhia Cousot.

### 2018-09-07 2018-ModelCheckingPNets/checking.tex
2 more drawings

@@
 
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=0.8\columnwidth]{figures/BIPspec-ArchFailureTimerMax-v2}
+  \caption{The BIP specification of the Failure Monitor architecture}
+  \label{schema:ArchFailure:BIP}
+\end{figure}
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=0.8\columnwidth]{figures/FailureTimerOA}
+  \caption{The Open Automaton of the Failure Monitor architecture}
+  \label{schema:ArchFailure:OA}
+\end{figure}
+
 \section{Describing pLTS}
@@
 $x_{i}\in X$ is a free variable bound in state formula $\varphi$.
-$\mu$ and $\nu$ are respectively the minimum fixed point and the maximum fixed point.\TODO{Tengfei: Must more explaination}
+$\mu$ and $\nu$ are respectively the minimum fixed point and the maximum fixed point.\TODO{Tengfei: Need more explanation}
 
@@
 
+\ERIC{this description is too operational (like a state machine), I would like a more logical description of the formula.
+One way is to use the vocabulary of ``Specification patterns'', like ``it is possible'', ``it is mandatory'', ``do something until some condition'', etc}
 At first, we can do $\langle start?M\rangle$ and then it enters a loop.

### 2018-09-10 2018-ModelCheckingPNets/checking.tex
new version with figure problem

--- 2018-09-06 2018-ModelCheckingPNets/checking.tex
@@
 \usepackage{subfigure}
-\usepackage{graphicx}
+\usepackage{figlatex}
+\usepackage{graphics}
 \usepackage{caption}
@@
 \setcounter{tocdepth}{3}
-\usepackage{graphicx}
 
@@
 \usepackage{palatino}
-\usepackage{tikz}
 \usetikzlibrary{shapes.geometric, arrows}
@@
 \section{Use-case: The BIP Failure-Timer architecture}
+
 \TODO{Describe here the full Failure-Timer architecture, as taken from the Avocs paper, including an informal presentation of the original BIP system, its full translation into a pNet system (pLTSs and pNet nodes), and the generated Open Automaton}
 \NOTE{All figures are already available from the Avocs paper sources.}
+
+The BIP architecture includes two kinds of components, coordinator component and operand component.
+The operand component just has some ports used to communicate with other component.
+While the coordinator components don't only have some ports, but they include a parameterised labelling transition system (pLTS) in them.
+In a pLTS, some nodes and edges between these nodes are built to describe the coordinator component.
+In a pLTS, a node denotes the state of the component, while a edge means the transition from one state to another.
+Specifically, a port in a coordinator component is used to label a transition, and the number of transitions is the same as that of ports.
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=0.8\columnwidth]{figures/BIPspec-ArchFailureTimerMax-v3.pdf}
+  \caption{The BIP specification of the Failure Monitor architecture}
+  \label{schema:ArchFailure:BIP}
+\end{figure}
+
+Fig.~\ref{schema:ArchFailure:BIP} shows the BIP specification of the Failure-Timer architecture from~\cite{xudong2017smt}.
+$Timer$ and $Controller$ are the coordinator components, and $B$ is an operand component.
+$Timer$ has four ports, like $start$, $tick$, $resume$ and $timeout$, and these ports are labelling the transitions between the two states $t_{0}$, and $t_{1}$.
+And $Ctrl$ has four ports, like $fail$, $reset$, $resume$ and $timeout$, and these ports are labelling the transitions between the three states $s_{0}$, $s_{1}$ and $s_{2}$.
+The operand component $B$ has three ports $resume$, $fail$ and $finish$.
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=0.8\columnwidth]{figures/FailureTimerOA.pdf}
+  \caption{The Open Automaton of the Failure Monitor architecture}
+  \label{schema:ArchFailure:OA}
+\end{figure}
+
+In~\cite{xudong2017smt}, an approach is present to unfold the open pNet to open automata.
+Fig.~\ref{schema:ArchFailure:OA} shows the open automaton unfolded from the Failure-Timer architecture in Fig~\ref{schema:ArchFailure:BIP}.
+The state is the composition of the states of each pLTS in the coordinator component, while the transition is labelled with a composition of the corresponding action in each component.
+For example, in the BIP specification, $Timer.start$ synchronises with $Ctrl.fail$, because there is a connector between the two ports.
+When occurrence of the transition $s_{0}\xrightarrow{fail}s_{1}$ will trigger the execution of the transition $t_{0}\xrightarrow{start, t:=0}t_{1}$.
+At the same time, the port $Ctrl.fail$ will synchronise with $B.fail$.
+The connected ports in Failure-Timer architecture form a synchronisation vector.
+The synchronisation will return to a special action, which can be used to label a transition.
 
@@
 	\item $S$ is a set of states, and $s_{0}\in S$ is the initial state.
-	\item $\rightarrow \subseteq S\times L\times S$ is the transition relation, with $L$ the set of labels of form $<\alpha, e_{b}, (x_{j} := e_{j})^{(j\in J)}>$, where $\alpha\in A_{V}$ is a parameterised action, $e_{b}\in B_{V}$ is a guard, and expression $E_{P}\cup A_{P}$ are assigned to $x_{j}$.
-If $s\xrightarrow{<\alpha, e_{b}, (x_{j}:=e_{j})^{j\in J}>}s' \in \rightarrow$, then $vars(e_{b})\subseteq vars(s)\cup vars(\alpha)$, and $\forall j\in J.
+	\item $\rightarrow \subseteq S\times L\times S$ is the transition relation, with $L$ the set of labels of form $\langle\alpha, e_{b}, (x_{j} := e_{j})^{(j\in J)}\rangle$, where $\alpha\in A_{V}$ is a parameterised action, $e_{b}\in B_{V}$ is a guard, and expression $E_{P}\cup A_{P}$ are assigned to $x_{j}$.
+If $s\xrightarrow{\langle\alpha, e_{b}, (x_{j}:=e_{j})^{j\in J}\rangle}s' \in \rightarrow$, then $vars(e_{b})\subseteq vars(s)\cup vars(\alpha)$, and $\forall j\in J.
 vars(e_{j})\subseteq vars(s)\wedge x_{j}\in vars(s')$.
@@
 $x_{i}\in X$ is a free variable bound in state formula $\varphi$.
-$\mu$ and $\nu$ are respectively the minimum fixed point and the maximum fixed point.\TODO{Tengfei: Must more explaination}
+$\mu$ and $\nu$ are respectively the minimum fixed point and the maximum fixed point.\TODO{Tengfei: Must more explaination}\NOTE{Done}
 
@@
 In this case study, intuitively the timer finally returns to the initial state after some execution steps.
-The property can be expressed by pM$\mu$ formula:
+The property can be expressed by a pM$\mu$ formula:
 
@@
 
-At first, we can do $\langle start?M\rangle$ and then it enters a loop.
-After that, either we can do a $timeout$, and then it is done and the result is true.
+\ERIC{this description is too operational (like a state machine), I would like a more logical description of the formula.
+One way is to use the vocabulary of ``Specification patterns'', like ``it is possible'', ``it is mandatory'', ``do something until some condition'', etc}
+At first, we can do $\langle start?M\rangle$ and then it is mandatory to enters a loop with an assignment $t := M$.
+In the loop, it is possible for us to do a $timeout$ until  $t$ is equal to 0, and then it is done and the result is true.
 Or we can do a $tick$ and then we continue the loop with decrementing the value $t$ by one.
@@
 
-\TODO{Tengfei: Be more precise}
+\TODO{Tengfei: Be more precise}\NOTE{Done}
 
@@
 A formula is said to be alternation-free, when the alternation depth is one, without mutually recursive greatest and least fixed-point operators.
-A formula expressed with pM$\mu$ is alternation-free.
-But the formula with first-order $\mu$-calculus have to deal with alternation depth.\TODO{definition of alternation depth]}
-\NOTE{A formula expressed with pM$\mu$ is alternation-free. !!!NO}
+In the Timer example, the alternation depth is 1.
+\TODO{definition of alternation depth]}
 
@@
 \subsection{The difference between pLTS and open automata}
+ pLTS is a labelling transition system with parameterised action.
+Open pNet is a composition of some pLTSs with synchronisation vector and some holes.
+A BIP architecture of an open pNet includes coordinator components and some operand components.
+An open automaton is formed by the unfolding of an open pNet.
 
@@
 	\caption{$close(s)$}
-	\label{alg:algorithm1}
+	\label{alg:algorithm2}
 \end{algorithm}
@@
 	\caption{check(s)}
-	\label{alg:algorithm2}
+	\label{alg:algorithm3}
 \end{algorithm}
@@
 \begin{thebibliography}{4}
+	\bibitem{xudong2017smt}Xudong Qin, Simon Bliudze, Eric Madelaine, Min Zhang. Using SMT engine to generate Symbolic Automata -Extended version. [Research Report] RR-9177, Inria
 

### 2018-09-11 2016-Weak-FH-Bisim/WeakBisim.tex
modifs
update tres leger pages 12-15

@@
 	\includegraphics[width=\linewidth]{XFIG/Bisim}
-%	\TODO{J'ai ajoute les predicats. Il reste a dessiner la ``couverture'' si j'y arrive...}
 \end{minipage}
@@
 The predicates on the transition will be obtained both from the predicates on the \pLTS s transitions and from the
+\TODO{Ce paragraph a eu un probleme, je ne sais pas quand.... Vous avez une vieille version sous la main ?}
 This allows us to derive a bismulation theory for open \pNet s.
@@
   \label{OT:ABP}
-At the upper level, the $ABP$ pNet has 2 holes and and $Protocol$ has
-a subnet. One of its possible open transition (synchronizing the hole $P$
+At the upper level, the $ABP$ pNet has 2 holes and $Protocol$ has
+a subnet. One of its possible open transitions (synchronizing the hole $P$
 with the \emph{Protocol}) is:
@@
 
+\TODO{Ceci n'est pas nouveau, n'est-ce pas, est-ce utile pour le lecteur ici ? Ou est-ce qu'on bouge tous ces ``details techniques'' dans une annexe ? Si oui, je refais avec un morceau de ABP}
 \begin{example} \emph{Using the operational rules to compute
@@
 
-\begin{figure}[bh]
+\begin{figure}[h]
 \begin{mathpar}
@@
 \subsection{Computing and using open automata}
-\TODO{REMOVE?}
+\TODO{REMOVE?  published at Avocs, we can shorten and add a bibref}
 In this section we present a simple algorithm to construct the open
@@
 under reasonable conditions this automaton is finite.
-
-% \TODO{Eric: refine the algorithm description - \ERIC{Done, can you check ?}}
 
@@
 
-\subsection{Bisimulation for open \pNet s and Composability}
+\subsection{Bisimulation for open pNets and Composability}
 \label{section:bisimulation-PN}

### 2018-09-12 2018-ModelCheckingPNets/checking.tex

@@
 \setcounter{tocdepth}{3}
+\usepackage{mathpartir}
 
@@
 
-\begin{figure}
+\begin{figure}[ht]
   \centering
-	\begin{tikzpicture}[->, shorten >=2pt, >=stealth, node distance=3cm,
-	noname/.style={ellipse, minimum width=5em, minimum height=3em,draw}]
-	\node[noname] (1)                                             {$s_{0}$};
-	\node[noname] (2) [right=of 1]                                {$s_{1}$};
-
-	\path 	(1) edge [bend left]                  node[above] {$[true],\langle start?M\rangle,\{t:=M\}$} (2)
-	(2) edge [bend left]                  node[below] {$[t=0], \langle timeout\rangle$} (1)
-	(2) edge 			               node[above] {$\langle resume\rangle$} (1);
-	\path[->] (2) edge [in=-10,out=20,loop] coordinate[pos=0.52] (midp) node[right] {$[t>0], \langle tick\rangle, \{t:=t-1\}$} (2);
-
-	\end{tikzpicture}
+  \includegraphics[width=0.8\columnwidth]{figures/TimerpLTS.eps}
   \caption{The pLTS of the Timer component}
+  \label{schema:Timer:pLTS}
 \end{figure}
-
-\subsubsection{Semantics of pLTS}
 
@@
 		\hline 		
-	Action formula 	&     $\alpha ::= \{\{c(arg_{1}, ..., arg_{n}), \tau\}\mid arg_{i}=?x\ |\ !e\  \}$                  \\
+	Action formula 	&     $\alpha ::= \{c(arg_{1}, ..., arg_{n})\mid arg_{i}=?x\mid\ !e\mid \tau\}$                  \\
 	& $|\ \neg\alpha \ |\ \alpha_{1}\vee\alpha_{2}\ |\ \alpha_{1}\wedge\alpha_{2}$   \\ 	\hline
@@
  where, $c$ is an action name expressing the communication port.
-$arg_{i}$ is a list of arguments, and each $arg_{i}$ is either a send expression $!e$, or a receive variable $?x$.
-An action $\alpha$ is a parameterised action $c(arg_{i})$ or a silent action $\tau$.
+$arg_{i}$ is a list of arguments, and each $arg_{i}$ is either a send expression $!e$, a receive variable $?x$ or a silent action $\tau$.
+An action $\alpha$ is a parameterised action $c(arg_{i})$.
 $p$ is an atomic proposition and $X$ is a set of variables.
@@
 
-We employ the case study from timer component\cite{mavridou2016architectrue}.
+We employ the case study from timer component~\cite{mavridou2016architectrue}.
 A liveness property defines that good thing finally happens.
@@
 One way is to use the vocabulary of ``Specification patterns'', like ``it is possible'', ``it is mandatory'', ``do something until some condition'', etc}
-At first, we can do $\langle start?M\rangle$ and then it is mandatory to enters a loop with an assignment $t := M$.
-In the loop, it is possible for us to do a $timeout$ until  $t$ is equal to 0, and then it is done and the result is true.
-Or we can do a $tick$ and then we continue the loop with decrementing the value $t$ by one.
+
+At first, the timer starts with receiving a value $M$, and then it is mandatory to enters a loop with an assignment $t := M$.
+In the loop $\mu$, it is possible for the timer to return true until the time is out $\langle timeout\rangle$, and it is done.
+Or it will continue the loop with decreasing the value $t$ by one when the timer ticks again $\langle tick\rangle$.
 
@@
 \begin{figure}
-    \centering\includegraphics[width=5.5in]{figures/architectrue.jpeg} 
+    \centering\includegraphics[width=5.5in]{figures/architecture.pdf}
     \caption{Architecture of symbolic model checking}
@@
 
-\subsection{The difference between pLTS and open automata}
+\subsection{Open Automata}
+
+The semantics of open pNets will be defined  as an open automaton. An open
+automaton is an automaton where each transition composes transitions of several LTSs with action of some holes, the transition occurs if some predicates hold, and can involve a set of state modifications.
+
+\begin{definition}[Open transitions]
+	\label{def:OpenTransitions}
+	An \emph{open transition} over a set  $(S_i,s_{0 i}, \rightarrow_i)^{i\in
+	I}$ of LTSs, a
+	set $J$ of holes with sorts $Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is a structure of the form:	
+	\begin{mathpar}
+	\inferrule*[myfraction=\reddottedrule]
+	{\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
+		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred, \Post}
+	{s \xrightarrow {v}s'}
+	\end{mathpar}
+	Where $s, s'\in\mathcal{S}$ and for all
+        $i\in I$, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the
+	LTS $(S_i,s_{0 i}, \rightarrow_i)$, and $\xrightarrow{b_j}_j$
+        is a transition of the hole $j$, for any action $b_j$ in the
+        sort $Sort_j$. \Pred\ is a predicate
+	over the different variables of the
+	terms, labels, and states $s_i$, $b_j$, $s$, $v$. \Post\ is a set of equations that 
+	hold \emph{after the open transition}, they are represented as a substitution of the 
+	form $\{x_k\gets e_k\}^{k\in K}$ 
+	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
+	variables of the open transition.
+\end{definition}
+
+\begin{definition}[Open automaton]
+	\label{def:open-automaton}
+	An \emph{open automaton} is a structure\\ $A =
+	<LTS_i^{i\in I},J,\mathcal{S},s_0,\mathcal{T}>$ where:
+	\begin{itemize}
+		\item[$\bullet$]  $I$ and $J$ are  sets of indices,
+		\item[$\bullet$]  $LTS_i^{i\in I}$ is a family of LTSs,
+		\item[$\bullet$]   $\mathcal{S}$ is a set of states and $s_0$ an initial state
+		among $\mathcal{S}$,
+		\item[$\bullet$] $\mathcal{T}$ is a set of open transitions and for each
+		$t\in \mathcal{T}$ there exist $I'$, $J'$ with $I'\subseteq I$, $J'
+		\subseteq J$, such that $t$ is an open transition over $LTS_i^{i\in I'}$, $J'$,
+		and  $\mathcal{S}$.
+
+	\end{itemize}
+\end{definition}
+
+\begin{definition}[States of open pNets]\label{def-states}
+  A state of an open pNet is a tuple (not necessarily finite) of the
+  states of its leaves (in which we denote tuples
+  in structured states as $\triangleleft\ldots\triangleright$ for better readability).
+
+  For any pNet p, let $\overline{Leaves} = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be the set of pLTS at its leaves,
+  then $States(p) = \{\triangleleft s_i^{i\in L}
+  \triangleright| \forall i\in L. s_i \in S_i\}$.
+A pLTS being its own single leave:
+  $States(\mylangle S,s_0, \to\myrangle) = \{\triangleleft s \triangleright| s \in S\}$.
+
+The initial state is defined as:
+$InitState(p) = \triangleleft {{s_i}_0}^{i\in L}  \triangleright$.
+\end{definition}
+
+\paragraph{Predicates:}
+Let $\mylangle\overline{\pNet},\overline{S},\symb{SV}_k^{k\in K} \myrangle$
+be a pNet. Consider a synchronization vector $SV_k$, for $k\in K$. We define a
+predicate $\Pred$ relating the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
+\[\Pred(SV_k, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow
+\begin{array}{l}
+\exists {(a'_i)}^{i\in I},
+{(b'_j)}^{j\in J},v'.\, SV_k={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v'
+\\~~\land
+\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v'
+\end{array}\]
+In any other case (if the action families do not match or if there is no valuation of variables such that the above formula can be ensured) the predicate is undefined.
+
+This definition is not constructive but it is easy to build the predicate constructively by brute-force unification of the sub-pNets actions with the corresponding vector actions, possibly followed by a simplification step.
+
+ \subsection{The difference between pLTS and open automaton}
  pLTS is a labelling transition system with parameterised action.
-Open pNet is a composition of some pLTSs with synchronisation vector and some holes.
+An open pNet is a composition of some pLTSs and some holes, and a set of synchronization vector composites the action of an open pNet.
 A BIP architecture of an open pNet includes coordinator components and some operand components.
-An open automaton is formed by the unfolding of an open pNet.
+An open automaton is formed by the unfolding of an open pNet through the rules in~\cite{xudong2017smt}.
 
-\subsection{}
+ In order to check the model of open automata, the algorithm in the appendix have to be modified. There are two different things in the structure of open automaton and pLTS.
+ \subsubsection{Hole}
+ A hole in pNet is defined without states, but it involves in a transition, which is defined as $\{\xrightarrow{b_j}_j\}^{j\in J}$.
+The action $b_{j}$ is the action of a hole with an index $j$.
+The difference of holes from pLTS is whether a component involves in a set of states.
+However, each action in the hole belongs to a set of the parameterised action.
 
-\subsection{}
+ \subsubsection{Predicate}
+ A transition in a pLTS is consisted of a tuple with labelling $guard$, $parameterised\; action$, $assignment$ between two states.
+Formally, a transition is defined as $s\xrightarrow{\langle\alpha, e_{b}, (x_{j}:=e_{j})^{j\in J}\rangle}s'$.
+While an open transition in an open automaton is defined with labelling $Pred$ and $Post$ between a composition of states in pLTSs and holes.
+In the open transition, $Pred$ is a predicate over the different variables of the terms, labels, and states.
+Specifically, a predicate consists of a set of parameterised actions in pLTSs and actions in holes.
+In a pNet, some ports from each component have an immediate relationship, and these ports are connected each other.
+Also, one of these ports is treated as a action to trigger a transition in the pLTS or in a hole.
+A predicate is a synchronization vector from the action in each pLTS and each hole.
+
+\subsection{opM$\mu$}
+In order to check open automata, a new property language is present.
+The property language is called open parameterised modal $\mu$-calculus (opM$\mu$).
+We give the formal definition in Tab.~\ref{opmu}:
+
+\begin{table}
+	%	\multirow{2}{*}{Algorithme}
+	\setlength\tabcolsep{18pt}% default value is 6pt 
+	\centering 
+	\caption{Syntax of the opM$\mu$} \label{opmu}
+	\begin{tabular}{>{\bfseries}c| c } 
+		\hline 		
+	Action formula 	&     $\alpha ::= \{c(arg_{1}, ..., arg_{n})\mid arg_{i}=?x\mid\ !e\mid \tau\}$                  \\
+	& $|\ \neg\alpha \ |\ \alpha_{1}\vee\alpha_{2}\ |\ \alpha_{1}\wedge\alpha_{2}$   \\ 	\hline
+
+	Predicate 	&     $Pred ::= \{c_i(arg_{1}, ..., arg_{n})\mid arg_{j}=?x\mid\ !e\mid \tau\}$                  \\
+	& $|\ \neg\alpha \ |\ \alpha_{1}\vee\alpha_{2}\ |\ \alpha_{1}\wedge\alpha_{2}$   \\ 	\hline
+
+	State formula 	&  $\varphi ::= p \mid X \mid \neg\varphi \mid \varphi_{1}\wedge\varphi_{2}\ |\ \varphi_{1}\vee\varphi_{2} \ |\ [\alpha]\varphi \ |\ \langle\alpha\rangle\varphi$ \\ 
+	& $\exists x_{i}\varphi\ |\ \forall x_{i}\varphi\ |\ \mu X(e_{i}/x_{i})\varphi\ |\ \nu X(e_{i}/x_{i})\varphi$	\\ \hline 
+	\end{tabular} 
+\end{table}
+
+\subsection{The modified algorithm}
 

### 2018-09-14 2016-Weak-FH-Bisim/WeakBisim.tex
update TODOs
proof in progress

@@
 %\inferrule 
-\forall i \in [0\ldots n].\openrule
+\Bigg(\forall i \in [0\ldots n].\openrule
     {
@@
          {
-           \overline{\beta^2},\Pred^2,\Post^2 }
+           \overline{\beta^2},\Pred\,^2,\Post^2 }
          {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
@@
          {
-           \overline{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
+           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
          {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
+\Bigg)        
+       \Longleftrightarrow\\  \Bigg( 
+ \Big(\alpha = \tau \wedge  \vis{\overline{\beta^2}}=\emptyset \wedge \Pred\,^2 =\symb{True} \wedge \Post^2 =\symb{Id(s)}\Big) \Bigg) \bigvee  {
+\openrule
+         {
+           \overline{\gamma},
+		\Pred, \Post
+				 } {s \OTWeakarrow {\alpha} s'} \in\WT
+}
 \end{mathpar}
-such that\\
+where\\
 \begin{mathpar} 
-s=s^1_0 \wedge s^1_n=s^2_0 \wedge s'^2 = s^3_0 \wedge s^3_m=s'
-\\\\
+s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s', \quad
 \overline{\gamma}=\biguplus_{i=0}^n \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^m \vis{\overline{\beta^3_i}}
 \\
-\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred^2\subst{\Post_1}\land (\bigwedge_{i=0}^m\Pred^3_i\subst{\Post^2})\subst{\Post^1_i}
-
+\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\subst{\Post_1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\subst{\Post^1_i}
+\\
+\Post=({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K}
 \end{mathpar}
 
-\begin{mathpar}
-\Longleftrightarrow  \left \{ \begin{array}{l} 
-\alpha = \tau \wedge  \vis{\overline{\beta^2}}=\emptyset \wedge \Pred^2 =\symb{True} \wedge \Post^2 =\symb{Id(s)}\\
-\\
-\bigvee \\
-\\
-{
-\openrule
-         {
-           \overline{\gamma},
-		\Pred,
-				({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K} } 
-         {s \OTWeakarrow {\alpha} s'} \in\WT
-}
-\end{array}
-\right.
-\end{mathpar}
-
 \end{lemma}
 
-\begin{proof} ($\Rightarrow$) We proceed by induction by induction the number of transitions with which we  build  a weak transition (introduced in Definition \ref{def:buildweakOT}).
-The base case  is if $n=0$ and $m=0$ then 
+\begin{proof} ($\Rightarrow$) We proceed by induction the number of transitions $l$ with which we  build  a weak transition (introduced in Definition \ref{def:buildweakOT}). We have  $l=n+m+1$.
+\begin{itemize}
+\item The base case $l=1$ ($n=0$ and $m=0$) then obtain
 \begin{mathpar}
@@
 \end{mathpar} 
-and by rule (2) we have
+by rule (2) we have
  \begin{mathpar}
@@
 \end{mathpar} 
-For the inductive step, first we have by induction hypothesis that the formula is valid for some length $l$ such that $l=n+m+1$, we have 
-\TODO{I will complete}
-
-on other hand by rule (2) we have
+\item For the inductive step, first we have by induction hypothesis that the formula holds for some length $l$.
+Induction step is to infer that formula holds for transitions of length $l + 1$.
+In particular, for $n+1$ or $m+1$.
+
+First by using rule (2) (and by replacing $\alpha$ by $\tau$)  we can directly conclude :
 \begin{mathpar}
@@
 
-\noindent ($\Leftarrow$) We proceed also by induction on the depth of the inference of 
+Second by using rule (3) \TODO{To complete}
+
+\end{itemize}
+\noindent ($\Leftarrow$) We proceed also  by induction the number of transitions $l$ with which we  build  a weak transition.
+
+\begin{itemize}
+\item Basis: suppose that $\OTWeakarrow {\alpha}$ cannot be subdivided. So for a given weak transition:
+
 \begin{mathpar}
@@
 \end{mathpar}
-First, using rule (1) we can directly conclude \\
-
-Second by using rule (2),  
-\begin{mathpar}
-{ \openrule
-         {
-          \overline{\gamma} \!,\Pred,\Post
-				 } {s \OTWeakarrow {\alpha} s'} \in \WT
-}
-\end{mathpar}
-implies that 
+W have two cases:
+\begin{itemize}
+\item either $\alpha = \tau$, $s=s'$, $\overline{\beta}=\emptyset$, $\Pred = \symb{True}$ and $\Post=\symb{Id}(s)$. \TODO{Conclusion?}
+
+\item Or we can directly conclude by rule (2) that we have
 \begin{mathpar}
@@
 \end{mathpar}
-such that $\overline{\gamma} = \vis{\overline{\beta}}$.\\
-Finally by using rule (3) we have
+such that $\overline{\gamma} = \vis{\overline{\beta}}$
+\end{itemize}
+\item Step: by using rule (3) we can rewrite a weak transition:
+
+\begin{mathpar}
+{ \openrule
+         {
+           \overline{\gamma}\!,\Pred,\Post
+				 } {s \OTWeakarrow {\alpha} s'} \in \WT
+}
+\end{mathpar}
+
+as
+
 \begin{mathpar}
@@
          {
-           \overline{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
+           \overline{\gamma_3},\Pred_3,\Post_3 }
          {s_2 \OTWeakarrow {\tau} s'} \in\!\WT
-\\
-\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
+%\\
+%\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
 }{}
 \end{mathpar}
-and by induction hypothesis this means that we have first,
+
+such that \\
+$\overline{\gamma}=\overline{\gamma_1} \dotcup \overline{\gamma_2} \dotcup \overline{\gamma_3}$, 
+$\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}$, and $\Post=$ \\
+
+By induction hypothesis and simplification we have: \\
+
 \begin{mathpar}
@@
 
-\end{mathpar}
-
-implies
-
-\begin{mathpar}
+\Rightarrow
+
 \forall i \in [0\ldots n_1].\openrule
@@
 
-such that\\
+where 
 \begin{mathpar} 
@@
 
-Secondly,
+and
+
+\begin{mathpar}
+%\inferrule{
+\openrule
+         {
+           \overline{\gamma_3},\Pred_3,\Post_3   }
+         {s_2 \OTWeakarrow {\tau} s'} \in\! \WT
+
+\Rightarrow
+
+\forall i \in [0\ldots m_1].\openrule
+    {
+       \overline{\beta^3_i},\Pred^3_i,\Post^3_i   }
+         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}         
+\end{mathpar}
+where
+
+\begin{mathpar} 
+s_2=s^3_0 \wedge s^1_{m_1}=s' \quad
+\overline{\gamma_3}=\biguplus_{i=0}^{m_1} \vis{\overline{\beta^3_i}} 
+\quad
+\Pred_3=\bigwedge_{i=0}^{m_1}\Pred^3_i\quad \Post_3= \biguplus_{i=0}^{m_1} \Post_i^3
+\end{mathpar}
+
+and
+
 \begin{mathpar}
@@
 
-\end{mathpar}
-implies
-\begin{mathpar}
-\forall i \in [0\ldots n_2].\openrule
+\Rightarrow
+\Bigg(\forall i \in [0\ldots n_2].\openrule
     {
        \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
-         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
-\quad
+         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}  \wedge
+
 \openrule
@@
          {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
-\quad \wedge\\
+ \wedge
 \forall i \in [0\ldots m_2].\openrule
@@
          {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
+\Bigg)         
 \end{mathpar}
-such that\\
+where\\
 \begin{mathpar} 
@@
 \end{mathpar}
-Finally,
-\begin{mathpar}
-%\inferrule{
-\openrule
-         {
-           \overline{\gamma_3},\Pred_3,\Post_3   }
-         {s_2 \OTWeakarrow {\tau} s'} \in\! \WT
-
-\end{mathpar}
-
-implies
-
-\begin{mathpar}
-\forall i \in [0\ldots m_1].\openrule
-    {
-       \overline{\beta^3_i},\Pred^3_i,\Post^3_i   }
-         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}         
-\end{mathpar}
-
-such that\\
-\begin{mathpar} 
-s_2=s^3_0 \wedge s^1_{m_1}=s' \quad
-\overline{\gamma_3}=\biguplus_{i=0}^{m_1} \vis{\overline{\beta^3_i}} 
-\quad
-\Pred_3=\bigwedge_{i=0}^{m_1}\Pred^3_i\quad \Post_3= \biguplus_{i=0}^{m_1} \Post_i^3
-\end{mathpar}
-
-\end{proof}
-
-------------------------------------------------------
 

### 2018-09-14 2016-Weak-FH-Bisim/WeakBisim.tex
a bit of informal description before meeting

--- 2018-09-11 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 \item \TODO{proposition Ludo \& Rabea: \pNet -> P,Q dans les formules pour que ce soit moins long}
+\item related works
 \end{itemize}
@@
 \item[X] reorga sec weak bisim + thm -> 10 Juil
-\item  intro et orga globale du papier -> fin aout
+\item[X]  intro et orga globale du papier -> fin aout
+\item[NEW] explication dans semantique open pnets et composition
 \end{itemize}
@@
 \end{itemize}
-=== en parallele
 
@@
 Now we define
-pNet nodes, as constructors for hierarchical behavioural structures.
+pNet nodes as constructors for hierarchical behavioural structures.
 A pNet has a set of sub-pNets that can be either pNets or pLTSs, and a
-set of Holes, playing the role of process parameters.
-
-A composite pNet consists of a set of sub-pNets exposing
-a set of actions, each of them synchronising actions in each of
-the sub-pNets. The synchronisation between global actions and
-internal actions is given by  \emph{synchronisation vectors}: a
+set of Holes, playing the role of process parameters. A pNet is thus a composition operator that can receive processes as parameters; it expresses how the actions of the sub-processes synchronise.
+
+Each sub-pNets expose
+a set of actions, called \emph{internal actions}. The synchronisation between global actions exposed by the pNet and
+internal actions of its sub-pNets is given by  \emph{synchronisation vectors}: a
 synchronisation vector synchronises one or several internal actions, and
@@
 We now define the structure of pNets, the following definition relies on the definition 
-of holes, leaves and sorts provided below in Definition~\ref{def-sortholeleave}.
+of holes, leaves and sorts formalised below in Definition~\ref{def-sortholeleave}.
+Informally, holes are process parameters, leavs provide the set of pLTSs at the leaves of the hierarchical structure of a pNet, and sorts give the signature of a pNete, i.e.
+the actions it exposes.
 

### 2018-09-14 2016-Weak-FH-Bisim/WeakBisim.tex
proof in progress second attempt

@@
 \item \TODO{proposition Ludo \& Rabea: \pNet -> P,Q dans les formules pour que ce soit moins long}
-\item related works
 \end{itemize}
@@
 \item[X] reorga sec weak bisim + thm -> 10 Juil
-\item[X]  intro et orga globale du papier -> fin aout
-\item[NEW] explication dans semantique open pnets et composition
+\item  intro et orga globale du papier -> fin aout
 \end{itemize}
@@
 \end{itemize}
+=== en parallele
 
@@
 \end{mathpar}
+
+ --------------------------------
+
+First, using rule (1) we can directly conclude \\
+
+Second by using rule (2),  
+\begin{mathpar}
+{ \openrule
+         {
+          \overline{\gamma} \!,\Pred,\Post
+				 } {s \OTWeakarrow {\alpha} s'} \in \WT
+}
+\end{mathpar}
+implies that 
+.\\
+Finally by using rule (3) we have
+\begin{mathpar}
+\inferrule{
+\openrule
+         {
+           \overline{\gamma_1},\Pred_1,\Post_1   }
+         {s \OTWeakarrow {\tau} s_1} \in\! \WT
+\quad
+\openrule
+         {
+           \overline{\gamma_2},\Pred_2,\Post_2  }
+         {s_1 \OTWeakarrow {\alpha} s_2} \in\! \WT
+\quad
+\openrule
+         {
+           \overline{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
+         {s_2 \OTWeakarrow {\tau} s'} \in\!\WT
+\\
+\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
+}{}
+\end{mathpar}
+and by induction hypothesis this means that we have first,
+\begin{mathpar}
+%\inferrule{
+\openrule
+         {
+           \overline{\gamma_1},\Pred_1,\Post_1   }
+         {s \OTWeakarrow {\tau} s_1} \in\! \WT
+
+\end{mathpar}
+
+implies
+
+\begin{mathpar}
+\forall i \in [0\ldots n_1].\openrule
+    {
+       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
+         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}         
+\end{mathpar}
+
+such that\\
+\begin{mathpar} 
+s=s^1_0 \wedge s^1_{n_1}=s_1 \quad
+\overline{\gamma_1}=\biguplus_{i=0}^{n_1} \vis{\overline{\beta^1_i}} 
+\quad
+\Pred_1=\bigwedge_{i=0}^{n_1}\Pred^1_i\quad \Post_1= \biguplus_{i=0}^{n_1} \Post_i^1
+\end{mathpar}
+
+Secondly,
+\begin{mathpar}
+\openrule
+         {
+           \overline{\gamma_2},\Pred_2,\Post_2  }
+         {s_1 \OTWeakarrow {\alpha} s_2} \in\! \WT
+
+\end{mathpar}
+implies
+\begin{mathpar}
+\forall i \in [0\ldots n_2].\openrule
+    {
+       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
+         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
+\quad
+\openrule
+         {
+           \overline{\beta^2},\Pred^2,\Post^2 }
+         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
+\quad \wedge\\
+\forall i \in [0\ldots m_2].\openrule
+         {
+           \overline{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
+         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
+\end{mathpar}
+such that\\
+\begin{mathpar} 
+s_1=s^1_0 \wedge s^1_n=s^2_0 \wedge s'^2 = s^3_0 \wedge s^3_{m_2}=s_2
+\\\\
+\overline{\gamma}=\biguplus_{i=0}^{n_2} \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^{m_2} \vis{\overline{\beta^3_i}}
+\\
+\Pred=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred^2\subst{\Post_1}\land (\bigwedge_{i=0}^{m_2}\Pred^3_i\subst{\Post^2})\subst{\Post^1_i}
+
+\end{mathpar}
+Finally,
+\begin{mathpar}
+%\inferrule{
+\openrule
+         {
+           \overline{\gamma_3},\Pred_3,\Post_3   }
+         {s_2 \OTWeakarrow {\tau} s'} \in\! \WT
+
+\end{mathpar}
+
+implies
+
+\begin{mathpar}
+\forall i \in [0\ldots m_1].\openrule
+    {
+       \overline{\beta^3_i},\Pred^3_i,\Post^3_i   }
+         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}         
+\end{mathpar}
+
+such that\\
+\begin{mathpar} 
+s_2=s^3_0 \wedge s^1_{m_1}=s' \quad
+\overline{\gamma_3}=\biguplus_{i=0}^{m_1} \vis{\overline{\beta^3_i}} 
+\quad
+\Pred_3=\bigwedge_{i=0}^{m_1}\Pred^3_i\quad \Post_3= \biguplus_{i=0}^{m_1} \Post_i^3
+\end{mathpar}
+
+\end{itemize}
+\end{proof}
+
+------------------------------------------------------
 

### 2018-09-14 2016-Weak-FH-Bisim/WeakBisim.tex
during meeting

--- 2018-09-14 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 \section*{Status and TODO list}
+Conventions
+[14/9/2018]
+
+Dans le texte pas de $\backslash$ devant pNet et pLTS
+
+pNet devient P ou Q dans les equations; on garde $pLTS$
+
+\medskip
+
 TODOS et deadline
@@
 
-\item \TODO{uniformiser pNet \pNet pNet s \pNet s (dans le texte et les formules!)}
-
-\item \TODO{proposition Ludo \& Rabea: \pNet -> P,Q dans les formules pour que ce soit moins long}
 \item related works
@@
 \item[X]  intro et orga globale du papier -> fin aout
-\item[NEW] explication dans semantique open pnets et composition
+\item[partial] explication dans semantique open pnets et composition
+\item uniformisation pNet P Q
 \end{itemize}
@@
 \begin{itemize}
-\item nettoyage -> 5 juil
+\item[X] nettoyage (1/2) -> 5 juil
+\item nettoyage exemple et algo de calcul
 \item example -> fin aout -> qq transitions dans l abp
@@
 \end{itemize}
-%=== 20 Avril?
+
 \medskip
@@
 \begin{itemize}
-\item preuve transitivite -> 10 juil
-\item proofs of new theorems -> fin juillet
+\item preuve transitivite -> 20 sept
+\item proofs of new theorems -> oct?
 %\item [x] uniformiser p et P pour les pnets 
@@
 
-\begin{theorem}[Context equivalencefor  weak bisimulation]\label{weak-thm-ctxt-eq}
+\begin{theorem}[Context equivalence for  weak bisimulation]\label{weak-thm-ctxt-eq}
 	Consider two weak FH-bisimilar open pNets:
@@
 
-\TODO{Here we should include:
-  %% \\  - A sufficient condition for an open PNet to preserve Weak-FH,
-  %% including: 1) no non-deterministic Tau-choice in the pLTSs, 2) a
-  %% synch vector propagating Tau from a subnet $pNet_i$ mandatory
-  %% everytime $pNet_i$ can do some visible action in the current
-  %% context, 3) if we have a vector <Tau, -, a, - > --> b with ``a'' a visible
-  %% action of some CLOSED subnet, then b=Tau. 
-  \\  - the corresponding Congruence theorem
-  \\- An example
-}
-
 \section{Conclusion and Discussion}
@@
 \appendix
-
-\section{Proof of associativity of Enable pNet.}
-\label{appendix:assoc}
-
-Using the usual encoding of the Lotos Enable operator (see
-Fig. \ref{schema:ABP-pnets}), we build now open automata for two  
-open pNets \texttt{P>>(Q>>R)} and \texttt{(P>>Q)>>R)}, and 
-prove their bisimilarity.
-\begin{figure}[t]
-\centerline{ % \includegraphics[width=0.5\linewidth]{XFIG/Struct-P-QR}
-% \includegraphics[width=0.35\linewidth]{XFIG/Struct-PQ-R}}
-  \includegraphics[width=0.60\linewidth]{XFIG/P-QR}
-  \hspace{5mm}
- \includegraphics[width=0.27\linewidth]{XFIG/PQ-R}}
-  \caption{Structure of the pNets for ``P>>(Q>>R) and (P>>Q)>>R''}
-  \label{schema:enable-assoc}
-\end{figure}
-
-The two open pNets are drawn in Fig. \ref{schema:enable-assoc}. To
-alleviate the drawing, we have only 
-  given one instance (C2) of the enable controller pLTSs, and one example of
-  the set of synchronisation vectors.
-
-  Below we give the two open automata for these pNets. In the
-  open-transitions in these 
-    automata, the predicates are very simple, and for readability
-    we show them directly in the transitions.
-    Remark that while the structure of the automaton states is useful
-    for their construction, it is not relevant later, so we have
-    dropped this structure when drawing the automaton.
-
-\begin{figure}[h]
-  \begin{minipage}{2cm}
-  \includegraphics[width=\linewidth]{XFIG/PQR-automaton}
-  \end{minipage}
-  \hspace{10mm}
-  \begin{minipage}{7cm}
-  \begin{eqnarray*}
-    OT_1 & = \openrule{0 \xrightarrow{l}_{C_3} 0
-    	\\\xrightarrow{a1}_P\\ a1\neq\delta(x)}
-    {\ostate{00} \OTarrow{a1} \ostate{00}}\\
-    OT_2 & = \openrule{
-                       0 \xrightarrow{\delta}_{C_3} 1, ~~
-                            0 \xrightarrow{l}_{C_4} 0,  ~~                 
-                            \{\xrightarrow{\delta(x1)}_P, ~~
-                            \xrightarrow{acc(x1)}_Q\}
-                      }
-                      {\ostate{00} \OTarrow{\underline{\delta(x1)}} \ostate{10}}    \\
-    OT_3 & = \openrule{0 \xrightarrow{l}_{C_4} 0,
-                        \\1 \xrightarrow{r}_{C_3} 1,\\
-                        \xrightarrow{a2}_Q,\\a2\neq\delta(x)
-                        }
-    {\ostate{10} \OTarrow{a2} \ostate{10}}\\
-    OT_4 & = \openrule{
-                       0 \xrightarrow{\delta}_{C_4} 1, \qquad
-                       1 \xrightarrow{r}_{C_3} 1, \qquad
-                       \{\xrightarrow{\delta(x2)}_Q, \qquad 
-                       \xrightarrow{acc(x2)}_R\} 
-                       }
-                      {\ostate{10} \OTarrow{\underline{\delta(x2)}} \ostate{11}}    \\
-    OT_5 & = \openrule{1 \xrightarrow{r}_{C_3} 1, \\1 \xrightarrow{r}_{C_4} 1, 
-    	\\\xrightarrow{a3}_R
-    	}
-    {\ostate{11} \OTarrow{a3} \ostate{11}}
-    \end{eqnarray*}
-  \end{minipage}
-  \caption{Open Automaton for the term ``P>>(Q>>R)''}
-  \label{schema:enable3bis}
-\end{figure}
-
-\begin{figure}[t]
-  \begin{minipage}{2cm}
-  \includegraphics[width=\linewidth]{XFIG/PQR2-automaton}
-  \end{minipage}
-  \hspace{10mm}
-  \begin{minipage}{7cm}
-  \begin{eqnarray*}
-    OT'_1 & = \openrule
-             {
-               0 \xrightarrow{l}_{C_3} 0,~~0 \xrightarrow{l}_{C_4} 0,~~
-               \{\xrightarrow{b1}_P\},~~ b1\neq\delta(y)
-               }
-             {\ostate{00} \OTarrow{b1} \ostate{00}}\\
-    OT'_2 & = \openrule
-             {
-                       0 \xrightarrow{l}_{C_5} 0, ~~
-                       0 \xrightarrow{\delta}_{C_6} 1,  ~~
-              \{\xrightarrow{\delta(y1)}_P,~~      \xrightarrow{acc(y1)}_Q\}~~ 
-                      }
-             {\ostate{00} \OTarrow{\underline{\delta(y1)}} \ostate{01}}\\
-    OT'_3 & = \openrule
-             {
-               0 \xrightarrow{l}_{C_5} 0,\\0 \xrightarrow{r}_{C_6} 0,
-               \\ \{\xrightarrow{b2}_Q\},\\b2\neq\delta(y)
-               }
-    {\ostate{01} \OTarrow{b2} \ostate{01}}\\
-    OT'_4 & = \openrule
-             {
-                       0 \xrightarrow{\delta}_{C_5} 1, ~~
-                       1 \xrightarrow{r}_{C_6} 1, ~~\{\xrightarrow{\delta(y2)}_Q, ~~
-                    \xrightarrow{accept(y2)}_R\} 
-                                 }
-             {\ostate{01} \OTarrow{\underline{\delta(y2)}} \ostate{11}}    \\
-    OT'_5 & = \openrule
-             {1 \xrightarrow{r}_{C_5} 1,\\\{\xrightarrow{b3}_R\}
-             	}
-             {\ostate{11} \OTarrow{b3} \ostate{11}}
-    \end{eqnarray*}
-  \end{minipage}
-%  \label{schema:enable5}
-\end{figure}
-
-In this example, we have no state variables in the pNets leaves, so we
-need no auxiliary predicate in the FH-bisimulation.
-
-Let us build a relation
-    $R = \{(A1_0,A2_0), (A1_1,A2_1), (A1_2,A2_2)\}$, and prove that
-    $R$ is a strong FH-bisimulation.
-
-    Pick e.g. transition $OT_1$ of automaton $A1$, we have
-    $A1_0 \xrightarrow{OT_1}_{A1} A1_0$. The matching transition from
-    $A2_0$ is $OT'_1$, with 
-    $A2_0 \xrightarrow{OT'_1}_{A2} A2_0$, the set of holes involved in
-    both transitions is $\{P\}$, and the resulting state is in the
-    bisimulation ($A1_0 ~ A2_0$).
-    The proof obligation is:
-
-    $$  a1\neq\delta(x) \implies
-         a1=b1 \implies b1\neq\delta(y) \land a1=b1 $$
-
-    The proof obligation for $OT_2$ versus $OT'_2$ is still simpler:
-
-    $$ \delta(x_1)=\delta(y_1) \land acc(x_1)=acc(y_1)
-       \implies \underline{\delta(x_1)}=\underline{\delta(y_1)} $$
-
-       the 3 other cases, and the 5 in the other direction, are left
-       to the reader. All are simple to prove, so $R$ is a
-       FH-bisimulation, and the initial states of the 2 pNets are equivalent.
-           \qed
-
-       This proof shows how the flattening induced by the open transitions makes the 
-       reasoning on hierarchical structures easy, while keeping a structured view of the 
-       compared systems.
-
-       \newpage
 

### 2018-09-17 2018-ModelCheckingPNets/checking.tex
opMu and formula

@@
 
+\newcommand{\Simon}{\\\hfill\mdash Simon}
+
+\newcommand{\noteSB}[2][color=green!40, size=\tiny]{\todo[#1]{{#2}\Simon}}
+\newcommand{\noteSBin}[2][inline,color=green!40]{\todo[#1]{{#2}\Simon}}
+\newcommand{\todoSB}[2][color=green!40, size=\tiny]{\todo[#1]{\textbf{To-do Simon:} {#2}}}
+\newcommand{\todoSBin}[2][inline,color=green!40]{\todo[#1]{\textbf{To-do Simon: } {#2}}}
+\newcommand{\Ludo}{\\\hfill\mdash Ludo}
+\newcommand{\noteLH}[2][color=orange!40, size=\tiny]{\todo[#1]{{#2}\Ludo}}
+\newcommand{\noteLHin}[2][inline,color=orange!40]{\todo[#1]{{#2}\Ludo}}
+\newcommand{\todoLH}[2][color=orange!40, size=\tiny]{\todo[#1]{\textbf{To-do Ludo:} {#2}}}
+\newcommand{\todoLHin}[2][inline,color=orange!40]{\todo[#1]{\textbf{To-do Ludo: } {#2}}}
+
+\newcommand{\noteIn}[2][inline,color=black!20]{\todo[#1]{{#2}}}
+
+\newcommand{\add}[2][Added]{\todo[color=blue!20, size=\tiny]{#1}{\color{blue}#2}}
+%% \newcommand{\remove}[2][Removed]{\todo[color=red!20, size=\tiny]{#1}}
+\newcommand{\remove}[2][Removed]{\todo[color=red!20, size=\tiny]{#1}{\color{red}\st{#2}}}
+\newcommand{\removeIn}[2][Removed]{\todo[color=red!10, inline]{{\color{red}#2}#1}}
+%% \newcommand{\replace}[3][Replaced]{\todo[color=blue!20, size=\tiny]{#1}{\color{blue}#3}}
+\newcommand{\replace}[3][Replaced]{\todo[color=blue!20, size=\tiny]{#1}{\color{blue}#3}{\color{red}\st{#2}}}
+
+\newcommand{\addSB}[1]{\add[Added by Simon]{#1}}
+\newcommand{\removeSB}[1]{\remove[Removed by Simon]{#1}}
+\newcommand{\removeSBin}[1]{\removeIn[Removed by Simon]{#1}}
+\newcommand{\replaceSB}[2]{\replace[Replaced by Simon]{#1}{#2}}
+
+\newcommand{\defn}[1]{Def.~\ref{defn:#1}}
+\newcommand{\defntwo}[2]{Defs~\ref{defn:#1} and \ref{defn:#2}}
+\newcommand{\fig}[1]{Fig.~\ref{fig:#1}}
+\newcommand{\Fig}[1]{Figure~\ref{fig:#1}}
+\newcommand{\figs}[2]{Fig.~\ref{fig:#1} and~\ref{fig:#2}}
+\newcommand{\tab}[1]{Tab.~\ref{tab:#1}}
+\newcommand{\eq}[1]{(\ref{eq:#1})}
+\newcommand{\res}[1]{(\ref{res:#1})}
+\newcommand{\ex}[1]{Ex.~\ref{ex:#1}}
+\newcommand{\exs}[2]{Ex.~\ref{ex:#1} and~\ref{ex:#2}}
+\newcommand{\secn}[1]{Sect.~\ref{secn:#1}}
+\newcommand{\rem}[1]{Note~\ref{rem:#1}}
+\newcommand{\lem}[1]{Lem.~\ref{lem:#1}}
+\newcommand{\cor}[1]{Cor.~\ref{cor:#1}}
+\newcommand{\thm}[1]{Th.~\ref{thm:#1}}
+\newcommand{\axs}[1]{Ax.~\ref{ax:#1}}
+% \newcommand{\ax}[2]{\ref{ax:#1}.\ref{ax:#1:#2}}
+\newcommand{\ax}[1]{Ax.~\ref{ax:#1}}
+\newcommand{\prop}[1]{Prop.~\ref{prop:#1}}
+\newcommand{\alg}[1]{Alg.~\ref{alg:#1}}
+\newcommand{\asmp}[1]{Ass.~\ref{asmp:#1}}
+
+% %%%%%%%%%%%%%%%%%%%%%
+
+\newcommand{\cA}{\ensuremath{\mathcal{A}}}
+\newcommand{\fA}{\ensuremath{\mathsf{A}}}
+\newcommand{\sA}{\ensuremath{\mathbb{A}}}
+\newcommand{\cB}{\ensuremath{\mathcal{B}}}
+\newcommand{\fB}{\ensuremath{\mathsf{B}}}
+\newcommand{\sB}{\ensuremath{\mathbb{B}}}
+\newcommand{\cC}{\ensuremath{\mathcal{C}}}
+\newcommand{\sC}{\ensuremath{\mathbb{C}}}
+\newcommand{\cD}{\ensuremath{\mathcal{D}}}
+\newcommand{\fD}{\ensuremath{\mathsf{D}}}
+\newcommand{\sD}{\ensuremath{\mathbb{D}}}
+\newcommand{\cE}{\ensuremath{\mathcal{E}}}
+\newcommand{\sE}{\ensuremath{\mathbb{E}}}
+\newcommand{\cF}{\ensuremath{\mathcal{F}}}
+\newcommand{\cG}{\ensuremath{\mathcal{G}}}
+\newcommand{\cH}{\ensuremath{\mathcal{H}}}
+\newcommand{\cI}{\ensuremath{\mathcal{I}}}
+\newcommand{\sI}{\ensuremath{\mathbb{I}}}
+\newcommand{\cM}{\ensuremath{\mathcal{M}}}
+\newcommand{\cN}{\ensuremath{\mathcal{N}}}
+\newcommand{\sN}{\ensuremath{\mathbb{N}}}
+\newcommand{\cP}{\ensuremath{\mathcal{P}}}
+\newcommand{\sP}{\ensuremath{\mathbb{P}}}
+\newcommand{\cQ}{\ensuremath{\mathcal{Q}}}
+\newcommand{\sQ}{\ensuremath{\mathbb{Q}}}
+\newcommand{\cR}{\ensuremath{\mathcal{R}}}
+\newcommand{\sR}{\ensuremath{\mathbb{R}}}
+\newcommand{\cS}{\ensuremath{\mathcal{S}}}
+\newcommand{\sS}{\ensuremath{\mathfrak{S}}}
+\newcommand{\cT}{\ensuremath{\mathcal{T}}}
+\newcommand{\fT}{\ensuremath{\mathsf{T}}}
+\newcommand{\sT}{\ensuremath{\mathbb{T}}}
+\newcommand{\cV}{\ensuremath{\mathcal{V}}}
+\newcommand{\fV}{\ensuremath{\mathsf{V}}}
+\newcommand{\sV}{\ensuremath{\mathbb{V}}}
+\newcommand{\sZ}{\ensuremath{\mathbb{Z}}}
+
+\newcommand{\mdash}[1][]{---#1}
+\newcommand{\ndash}{--}
+\newcommand{\ie}[1][\ ]{i.e.#1}
+\newcommand{\etc}[1][\ ]{etc.#1}
+\newcommand{\eg}[1][\ ]{e.g.#1}
+\newcommand{\cf}[1][\ ]{cf.#1}
+\newcommand{\wrt}[1][\ ]{w.r.t.#1}
+\newcommand{\resp}[1][\ ]{resp.#1}
+
+\newcommand{\bydef}[1]{\ensuremath{\stackrel{\mathit{\scriptscriptstyle def}}{#1}}}
+\newcommand{\suchthat}{\ensuremath{\,|\,}}
+\newcommand{\rightsuchthat}{\ensuremath{\,\right|\,}}
+\newcommand{\leftsuchthat}{\ensuremath{\,\left|\,}}
+\newcommand{\setdef}[2]{\ensuremath{\{{#1}\,|\,{#2}\}}}
+\newcommand{\setdefb}[2]{\ensuremath{\bigl\{{#1}\,\bigl|\,{#2}\bigr.\bigr\}}}
+\newcommand{\Setdef}[2]{\ensuremath{\Big\{{#1}\,\Big|\,{#2}\Big\}}}
+\newcommand{\goesto}[2][]{\ensuremath{\xrightarrow[#1]{#2}}}
+\newcommand{\notgoesto}[2][]{\ensuremath{\not\xrightarrow[#1]{\ \,#2}}}
+\newcommand{\non}[1]{\ensuremath{\overline{#1}}}
+
+\newcommand{\true} {\ensuremath{\mathtt{t\!t}}}
+\newcommand{\false}{\ensuremath{\mathtt{f\!f}}}
+\newcommand{\noop} {\ensuremath{\emptyset}} % \mathsf{skip}
+
+\newcommand{\ordbool}{\ensuremath{\sB^{<}}}
+\newcommand{\data}{\ensuremath{\sD}}
+\newcommand{\signature}{\ensuremath{\Sigma}}
+\newcommand{\variables}{\ensuremath{\cV}}
+\newcommand{\Talg}{\ensuremath{\cT_{\signature,\variables}}}
+\newcommand{\actions}[1]{\ensuremath{\cA_{#1}}}
+\newcommand{\guards}[1]{\ensuremath{\ordbool_{#1}}}
+\newcommand{\exprs}[1]{\ensuremath{\sE_{#1}}}
+\newcommand{\boolexprs}[1]{\ensuremath{\sB_{#1}}}
+\newcommand{\assigns}[1]{\ensuremath{\sA_{#1}}}
+\newcommand{\valuations}[1]{\ensuremath{\data^{#1}}}
+\newcommand{\val}[3][]{\ensuremath{#1{\sigma}^{#2}_{#3}}}
+
+\newcommand{\filter}[2][]{\ensuremath{\pi_{#1}({#2})}}
+
+\newcommand{\primeit}[1]{#1'}
+\newcommand{\doubleprimeit}[1]{#1''}
+
+\newcommand{\export}[1][]{\ensuremath{\varepsilon_{#1}}}
+\newcommand{\valdiff}[2]{\ensuremath{#1 \triangle #2}}
+\newcommand{\supp}[1]{\ensuremath{\mathrm{supp}(#1)}}
+\newcommand{\semopen}[1]{\ensuremath{[{#1}]}}
+\newcommand{\semclosed}[1]{\ensuremath{\llbracket{#1}\rrbracket}}
+\newcommand{\reachable}[1]{\ensuremath{\mathit{reachable}({#1})}}
+\newcommand{\IMextend}[2]{\ensuremath{#1 \ltimes #2}}
+\newcommand{\arcomp}{\oplus}
+\newcommand{\arequiv}{\equiv}
+\newcommand{\Arcomp}{\Bigoplus}
+\newcommand{\expmix}{\wedge}
+\newcommand{\order}{\leqslant}
+
 \usepackage{url}
@@
 %
-\author{Tengfei Li
-%\thanks{Corresponding author}%
-\and Eric Madelaine \and *
+\author{Tengfei?Li
+\and Eric?Madelaine \and *
 }
@@
 
-\section{Use-case: The BIP Failure-Timer architecture}
+\section{Use-case: The BIP Failure-Timer architecture}\label{Sec2:usecase}
 
@@
 
-At first, the timer starts with receiving a value $M$, and then it is mandatory to enters a loop with an assignment $t := M$.
-In the loop $\mu$, it is possible for the timer to return true until the time is out $\langle timeout\rangle$, and it is done.
-Or it will continue the loop with decreasing the value $t$ by one when the timer ticks again $\langle tick\rangle$.
+At first, a $start$ occurs with receiving a value $M$, and then it is mandatory to enters a loop with an assignment $t := M$.
+In the loop $\mu$, it is possible for the timer to return true until an action $timeout$ happens, and it is done.
+Or it will continue the loop with decreasing the value $t$ by one when the $tick$ again.
 
@@
 \begin{figure}
-    \centering\includegraphics[width=5.5in]{figures/architecture.pdf}
+    \centering\includegraphics[width=0.8\columnwidth]{figures/Architecture.pdf}
     \caption{Architecture of symbolic model checking}
@@
 
+\begin{definition}[pNets]\label{def-pnets}
+A pNet is a hierarchical structure where leaves are pLTSs and holes\footnote{Typing can 
+be added to pNets by defining and checking their interfaces, called 
+sort~\cite{HMZ-FORTE2016}}:
+$\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, J, \symb{SV}_k^{k\in 
+K}\myrangle$
+where
+\begin{itemize}
+\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets;
+%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which 
+%sub-pNets are indexed.
+
+\item[$\bullet$] $J$ is a set of indexes, called \emph{holes}.
+$I$ and $J$ are \emph{disjoint}: $I\!\cap\! J=\emptyset$,  $I\!\cup\! J\neq\emptyset$
+%\item[$\bullet$] $\Sort_j \subseteq \AlgAS$ is a set of action terms, denoting the 
+%\emph{sort} of
+%hole $j$.
+
+\item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
+  synchronisation vectors. % (\hl{$K\in\I_\P$}). 
+$\forall k\!\in\! K,
+  \symb{SV}_k\!=\SV{\!\alpha_{l}^{l\in I_k \uplus J_k}}{\alpha'_k}{g_k}$, where
+  $\alpha'_k\in \actions{\variables}$, $I_k\subseteq I$, $J_k\subseteq J$, and 
+  $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
+  J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
+$\alpha'_k$. The Boolean expression $g_k $, such that $\vars(g_k)\subseteq \bigcup_{l\in 
+I_k\uplus J_k}{\vars({\alpha_l})}$, is a guard associated to the vector.
+
+\end{itemize}
+We define the set of holes and leaves of a pNet as follows:
+  \begin{itemize}
+\item
+The set of holes $\Holes(\pNet_{i_1})$ of a pNet is the indexes of the holes of the pNet 
+itself plus the indexes of all the holes of its subnets (we suppose those indexes 
+disjoints).
+%
+%defined inductively; the sets of holes
+%in a pNet node and its subnets are all disjoint:
+%  \[\begin{array}{l}
+%\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset \\
+%\Holes(\mylangle \pNet_i^{i\in I}\!,\Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) 
+%=J\uplus{\displaystyle \bigcup_{i\in 
+%I}\Holes(\pNet_i)}\\
+%\forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
+%\forall i_1,i_2\in I.\,i_1\neq i_2\Rightarrow  
+%\Holes(\pNet_{i_1})\cap\Holes(\pNet_{i_2})=\emptyset
+%\end{array}\]
+\item
+The set of leaves of a pNet is the set of all pLTSs occurring in the structure, as an 
+indexed family of the form $\Leaves(\pNet)= \mylangle \pNet_i \myrangle^{i \in L}$.
+is said to be \emph{open}.
+\end{itemize}
+A pNet $Q$ is \emph{closed} if it has no hole: $\Holes(Q)=\emptyset$; else it
+is said to be \emph{open}.
+\end{definition}
+
 The semantics of open pNets will be defined  as an open automaton. An open
@@
 	\label{def:OpenTransitions}
-	An \emph{open transition} over a set  $(S_i,s_{0 i}, \rightarrow_i)^{i\in
-	I}$ of LTSs, a
-	set $J$ of holes with sorts $Sort_j^{j\in J}$, and a set of states $\mathcal{S}$ is a structure of the form:	
+	An \emph{open transition} over a
+	set $J$ of holes  and a set of states $\mathcal{S}$ is 
+	a structure of the form:	
 	\begin{mathpar}
 	\inferrule*[myfraction=\reddottedrule]
-	{\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
-		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred, \Post}
-	{s \xrightarrow {v}s'}
+	{	\beta_j^{j\in J}, \Pred, \Post}
+	{s \OTarrow {{\alpha}}s'}
 	\end{mathpar}
-	Where $s, s'\in\mathcal{S}$ and for all
-        $i\in I$, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the
-	LTS $(S_i,s_{0 i}, \rightarrow_i)$, and $\xrightarrow{b_j}_j$
-        is a transition of the hole $j$, for any action $b_j$ in the
-        sort $Sort_j$. \Pred\ is a predicate
+	Where $s, s'\in\mathcal{S}$ and $\beta_j\in\actions{\variables}$
+        is an action of the hole $j$. $v$ is a variable denoting the resulting action
+        of this open transition. \Pred\ is a predicate 
 	over the different variables of the
-	terms, labels, and states $s_i$, $b_j$, $s$, $v$. \Post\ is a set of equations that 
-	hold \emph{after the open transition}, they are represented as a substitution of the 
-	form $\{x_k\gets e_k\}^{k\in K}$ 
-	where $x_k$ are variables of $s'$, $s'_i$, and $e_k$ are expressions over the other 
-	variables of the open transition.
+	terms, labels, and states  $\beta_j$, $s$, $\alpha$. $\Post\in 
+	\assigns{\variables}$\ is 
+	a set of assignments that are the effects of the transition.
+Open transitions are identified modulo logical equivalence on their predicate.
 \end{definition}
@@
 	An \emph{open automaton} is a structure\\ $A =
-	<LTS_i^{i\in I},J,\mathcal{S},s_0,\mathcal{T}>$ where:
+	<J,\mathcal{S},s_0,\mathcal{T}>$ where:
 	\begin{itemize}
 		\item[$\bullet$]  $I$ and $J$ are  sets of indices,
-		\item[$\bullet$]  $LTS_i^{i\in I}$ is a family of LTSs,
 		\item[$\bullet$]   $\mathcal{S}$ is a set of states and $s_0$ an initial state
@@
 		$t\in \mathcal{T}$ there exist $I'$, $J'$ with $I'\subseteq I$, $J'
-		\subseteq J$, such that $t$ is an open transition over $LTS_i^{i\in I'}$, $J'$,
+		\subseteq J$, such that $t$ is an open transition over $J'$,
 		and  $\mathcal{S}$.
@@
   A state of an open pNet is a tuple (not necessarily finite) of the
-  states of its leaves (in which we denote tuples
-  in structured states as $\triangleleft\ldots\triangleright$ for better readability).
+  states of its leaves.
 
-  For any pNet p, let $\overline{Leaves} = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be the set of pLTS at its leaves,
+  For any pNet p, let $\Leaves(p) = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be 
+  the set of pLTS at its leaves,
   then $States(p) = \{\triangleleft s_i^{i\in L}
@@
 \paragraph{Predicates:}
-Let $\mylangle\overline{\pNet},\overline{S},\symb{SV}_k^{k\in K} \myrangle$
-be a pNet. Consider a synchronization vector $SV_k$, for $k\in K$. We define a
-predicate $\Pred$ relating the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
-\[\Pred(SV_k, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow
-\begin{array}{l}
-\exists {(a'_i)}^{i\in I},
-{(b'_j)}^{j\in J},v'.\, SV_k={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v'
-\\~~\land
-\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v'
-\end{array}\]
+Let
+$\mylangle\overline{\pNet},\overline{\Sort},\overline{\symb{SV}}\myrangle$
+be a pNet. Consider a synchronisation vector $\symb{SV}\in \overline{\symb{SV}}$. We 
+define a
+predicate $\Pred$ relating
+the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
+\begin{multline}
+\Pred_{\symb{sv}}(\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
+{\alpha'} {g}, \alpha_i^{i\in I}, \beta_j^{j\in J}, \alpha)\Leftrightarrow \\
+\forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, \beta_j=\beta'_j \land 
+\alpha=\alpha' 
+\land g
+\end{multline}
+
  In any other case (if the action families do not match or if there is no valuation of variables such that the above formula can be ensured) the predicate is undefined.
@@
 Specifically, a predicate consists of a set of parameterised actions in pLTSs and actions in holes.
-In a pNet, some ports from each component have an immediate relationship, and these ports are connected each other.
+\NOTE{In a pNet, some ports from each component have an immediate relationship, and these ports are connected each other.
 Also, one of these ports is treated as a action to trigger a transition in the pLTS or in a hole.
-A predicate is a synchronization vector from the action in each pLTS and each hole.
+A predicate is a synchronization vector from the action in each pLTS and each hole.}
 
 \subsection{opM$\mu$}
-In order to check open automata, a new property language is present.
-The property language is called open parameterised modal $\mu$-calculus (opM$\mu$).
-We give the formal definition in Tab.~\ref{opmu}:
+In order to check open automata, a new property language is present. The property language is called open parameterised modal $\mu$-calculus (opM$\mu$). We give the syntax in Tab.~\ref{opmu}:
 
@@
 		\hline 		
-	Action formula 	&     $\alpha ::= \{c(arg_{1}, ..., arg_{n})\mid arg_{i}=?x\mid\ !e\mid \tau\}$                  \\
+	Action formula of pLTS &     $\alpha ::= \{c(arg_{1}, ..., arg_{n})\mid arg_{i}=?x\mid\ !e\mid \tau\}$                  \\
 	& $|\ \neg\alpha \ |\ \alpha_{1}\vee\alpha_{2}\ |\ \alpha_{1}\wedge\alpha_{2}$   \\ 	\hline
 
-	Predicate 	&     $Pred ::= \{c_i(arg_{1}, ..., arg_{n})\mid arg_{j}=?x\mid\ !e\mid \tau\}$                  \\
-	& $|\ \neg\alpha \ |\ \alpha_{1}\vee\alpha_{2}\ |\ \alpha_{1}\wedge\alpha_{2}$   \\ 	\hline
+	Action formula of Hole &     $\beta ::= \{c(arg_{1}, ..., arg_{n})\mid arg_{j}=?x\mid\ !e\mid \tau\}$                  \\
+	& $|\ \neg\beta \ |\ \beta_{1}\vee\beta_{2}\ |\ \beta_{1}\wedge\beta_{2}$   \\ 	\hline
 
-	State formula 	&  $\varphi ::= p \mid X \mid \neg\varphi \mid \varphi_{1}\wedge\varphi_{2}\ |\ \varphi_{1}\vee\varphi_{2} \ |\ [\alpha]\varphi \ |\ \langle\alpha\rangle\varphi$ \\ 
-	& $\exists x_{i}\varphi\ |\ \forall x_{i}\varphi\ |\ \mu X(e_{i}/x_{i})\varphi\ |\ \nu X(e_{i}/x_{i})\varphi$	\\ \hline 
+	Action formula of pNet &     $\gamma ::= \{c\}\ |\ \neg\gamma \ |\ \gamma_{1}\vee\gamma_{2}\ |\ \gamma_{1}\wedge\gamma_{2}$   \\ 	\hline
+
+	Predicate &     $pred ::= \alpha\wedge \beta\wedge \gamma$   \\ 	\hline
+
+	 	&  $\varphi ::= p \mid X \mid \neg\varphi \mid \varphi_{1}\wedge\varphi_{2}\ |\ \varphi_{1}\vee\varphi_{2} $\\
+	 State formula & $\ |\ [\alpha]\varphi \ |\ \langle\alpha\rangle\varphi \ |\ [\beta]\varphi \ |\ \langle\beta\rangle\varphi \ |\ [\gamma]\varphi \ |\ \langle\gamma\rangle\varphi $  \\ 
+	& $\ |\ \exists x_{i}\varphi\ |\ \forall x_{i}\varphi\ |\ \mu X(e_{i}/x_{i})\varphi\ |\ \nu X(e_{i}/x_{i})\varphi$	\\ \hline 
 	\end{tabular} 
@@
 
+\TODO{One thing is how to distinguish the action of pLTSs, Holes and pNet, i.e. whose action does $\langle resume\rangle$ stand for?}
+
+An opM$\mu$ is defines as a property language that is used to describe the concurrent systems.
+$\alpha$ is an action formula from pLTS.
+$\beta$ is a Hole action formula.
+$\beta$ can be a $c(arg_i)$ with three kinds of parameter $?x, !e, \tau$,  or the composition of several $\beta$ formula with negation, disjunction and conjunction.
+$\gamma$ is an action formula from open transition, and it is defined as an action name or the negation of $gamma$, or the disjunction and conjunction of two $\gamma$ formula.
+A predicate, which is the disjunction of $\alpha$, $\beta$ and $\gamma$, labels an open transition.
+In the state formula, $[\beta]\varphi$, $\langle\beta\rangle\varphi$, $[\gamma]\varphi$ and $\langle\gamma\rangle\varphi$ are added into the list.
+
+An example of opM$\mu$ is the formula for open automaton in Sec.~\ref{Sec2:usecase}.  The formula can be expressed as follows:
+\begin{equation}\label{formula3}
+	\nu X(\langle fail?M\rangle\mu Y(M/t)(\langle resume\rangle X \vee \langle tick\rangle Y(t-1/t)\vee \langle ask\wedge reset\rangle true))
+\end{equation}
+First, a $fail$ occurs with receiving a value $M$, and then a $tick$ happens with decreasing $t$ by one.
+Or the system returns true after an $ask$ and the subsequent $reset$ occur.
+Otherwise, the system restarts after a $resume$ happens.
+
 \subsection{The modified algorithm}
 
-\section{Related work and Conclusion}
+\section{Related work}
+
+\section{ Conclusion}
 

### 2018-09-19 2016-Weak-FH-Bisim/WeakBisim.tex
proof version stable

@@
 \item \TODO{should we use iff/implies or LeftRightArrow/Rightarrow}
-
 \item related works
@@
     \WT>$ be the
-weak open automata derived from $A$.
+weak open automata derived from $A$.  For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:
 
@@
 \\
-\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\subst{\Post_1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\subst{\Post^1_i}
-\\
+\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\subst{\Post_1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\subst{\Post^1_i}\\
 \Post=({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K}
@@
 
-\begin{proof} ($\Rightarrow$) We proceed by induction the number of transitions $l$ with which we  build  a weak transition (introduced in Definition \ref{def:buildweakOT}). We have  $l=n+m+1$.
+\begin{proof} ($\Rightarrow$) We proceed by induction on the number of transitions $l$ with which we  build  a weak transition (introduced in Definition \ref{def:buildweakOT}), in particular we have  $l=n+m+1$.
 \begin{itemize}
-\item The base case $l=1$ ($n=0$ and $m=0$) then obtain
+\item The base case $l=1$, so $n=0$ and $m=0$, then obtain
 \begin{mathpar}
@@
 \end{mathpar} 
-by rule (2) we have
+by rule (2) we directly conclude 
  \begin{mathpar}
  % \mprset {vskip=.5ex}
-\inferrule{
- \openrule
-         {
-           \overline{\beta},\Pred,\Post}
-         {s \OTarrow {\alpha} s'} \in \mathcal{T}
-}
+%\inferrule{
+% \openrule
+%         {
+%           \overline{\beta},\Pred,\Post}
+%         {s \OTarrow {\alpha} s'} \in \mathcal{T}
+%}
 { \openrule
@@
 Induction step is to infer that formula holds for transitions of length $l + 1$.
-In particular, for $n+1$ or $m+1$.
-
-First by using rule (2) (and by replacing $\alpha$ by $\tau$)  we can directly conclude :
+In particular, for $n+1$ or $m+1$, by adding the transition:
 \begin{mathpar}
  % \mprset {vskip=.5ex}
-\inferrule{
+%\inferrule{
  \openrule
@@
          {s \OTarrow {\tau} s'} \in \mathcal{T}
-}
+%}
+\end{mathpar}
+
+First by using rule (2) we can directly conclude :
+\begin{mathpar}
+ % \mprset {vskip=.5ex}
+%\inferrule{
+% \openrule
+%         {
+%           \overline{\beta},\Pred,\Post}
+%         {s \OTarrow {\tau} s'} \in \mathcal{T}
+%}
 { \openrule
@@
 \end{itemize}
-\noindent ($\Leftarrow$) We proceed also  by induction the number of transitions $l$ with which we  build  a weak transition.
+\noindent ($\Leftarrow$) We proceed also  by induction on the number of transitions $l$ with which we  build  a weak transition.
 
@@
 \end{mathpar}
-W have two cases:
+We have two cases:
 \begin{itemize}
-\item either $\alpha = \tau$, $s=s'$, $\overline{\beta}=\emptyset$, $\Pred = \symb{True}$ and $\Post=\symb{Id}(s)$. \TODO{Conclusion?}
-
-\item Or we can directly conclude by rule (2) that we have
+\item either $\alpha = \tau$, $s=s'$, $\overline{\beta}=\emptyset$, $\Pred = \symb{True}$ and $\Post=\symb{Id}(s)$. So by rule (2) we have: 
+\begin{mathpar}
+{ \openrule
+         {
+           \emptyset,\symb{True},\symb{Id}(s)
+				 } {s \OTarrow {\tau} s} \in \mathcal{T}
+}
+\end{mathpar}
+\item Otherwise, by rule (2) we conclude that we have: 
 \begin{mathpar}
@@
 \end{mathpar}
-such that $\overline{\gamma} = \vis{\overline{\beta}}$
+where $\overline{\gamma} = \vis{\overline{\beta}}$
 \end{itemize}
@@
 $\overline{\gamma}=\overline{\gamma_1} \dotcup \overline{\gamma_2} \dotcup \overline{\gamma_3}$, 
-$\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}$, and $\Post=$ \\
-
-By induction hypothesis and simplification we have: \\
-
+$\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}$, and $\Post=$ \TODO{Voir comment l'exprimer}\\
+
+\begin{enumerate}
+
+\item By induction hypothesis and simplification we have: 
 \begin{mathpar}
 %\inferrule{
-\openrule
+\bigg( \openrule
          {
            \overline{\gamma_1},\Pred_1,\Post_1   }
-         {s \OTWeakarrow {\tau} s_1} \in\! \WT
-
+         {s \OTWeakarrow {\tau} s_1} \in\! \WT \bigg)
 \Rightarrow
-
-\forall i \in [0\ldots n_1].\openrule
+\bigg( \forall i \in [0\ldots n_1].\openrule
     {
        \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
-         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}         
+         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}         \bigg)
 \end{mathpar}
-
 where 
 \begin{mathpar} 
-s=s^1_0 \wedge s^1_{n_1}=s_1 \quad
+s=s^1_0 \wedge\, s^1_{n_1}=s_1 \quad
 \overline{\gamma_1}=\biguplus_{i=0}^{n_1} \vis{\overline{\beta^1_i}} 
@@
 
-and
-
+\item and
 \begin{mathpar}
 %\inferrule{
-\openrule
+\bigg( \openrule
          {
@@
          {s_2 \OTWeakarrow {\tau} s'} \in\! \WT
-
+\bigg)
 \Rightarrow
-
+\bigg( \forall i \in [0\ldots m_1].\openrule
+    {
+       \overline{\beta^3_i},\Pred^3_i,\Post^3_i   }
+         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}         \bigg)
+\end{mathpar}
+where
+\begin{mathpar} 
+s_2=s^3_0 \wedge s^1_{m_1}=s'\quad
+\overline{\gamma_3}=\biguplus_{i=0}^{m_1} \vis{\overline{\beta^3_i}}\quad
+\Pred_3\!=\!\bigwedge_{i=0}^{m_1}\Pred^3_i \quad \Post_3= \biguplus_{i=0}^{m_1} \Post_i^3
+\end{mathpar}
+
+\item and 
+\begin{mathpar}
+\bigg(\openrule
+         {
+           \overline{\gamma_2},\Pred_2,\Post_2  }
+         {s_1 \OTWeakarrow {\alpha} s_2} \in\! \WT\bigg)
+\Rightarrow
+\Bigg(\forall i \in [0\ldots n_2].\openrule
+    {
+       \overline{\beta'^1_i},\Pred\,'^1_i,\Post'^1_i   }
+         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}  \wedge
+
+\openrule
+         {
+           \overline{\beta'^2},\Pred\,'^2,\Post'^2 }
+         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
+ \wedge
+\forall i \in [0\ldots m_2].\openrule
+         {
+           \overline{\beta'^3_i},\Pred\,'^3_i,({x^3_k\gets e^3_k})^{k\in K'}    }
+         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
+\Bigg)         
+\end{mathpar}
+where\\
+\begin{mathpar} 
+s_1=s^1_0 \wedge s^1_n=s^2_0 \wedge s'^2 = s^3_0 \wedge s^3_{m_2}=s_2,
+\overline{\gamma_2}=\biguplus_{i=0}^{n_2} \vis{\overline{\beta'^1_i}} \dotcup  \vis{\overline{\beta'^2}} \dotcup \biguplus_{i=0}^{m_2} \vis{\overline{\beta'^3_i}}
+\\
+\Pred_2=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred\,^2\subst{\Post_1}\land (\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2})\subst{\Post^1_i}
+
+\end{mathpar}
+\end{enumerate}
+
+Therefore, we can conclude that:
+\begin{mathpar}
+\bigg( { \openrule
+         {
+           \overline{\gamma}\!,\Pred,\Post
+				 } {s \OTWeakarrow {\alpha} s'} \in \WT
+}\bigg)
+\!\Rightarrow\!
+\Bigg(\!\forall i\! \in\! [0\ldots(n_1\!+\!n_2)].\openrule
+    {
+       \overline{\beta'^1_i},\Pred\,''^1_i,\Post''^1_i   }
+         {s^1_i \OTarrow {\tau} s^1_{i+1}}\! \in\!\mathcal{T} \wedge
+
+\openrule
+         {
+           \overline{\beta'^2},\Pred\,''^2,\Post''^2 }
+         {s^2 \OTarrow {\alpha} s'^2}\! \in\! \mathcal{T}
+\!\wedge
+\forall i\! \in\! [0\ldots(m_1\!+\!m_2)].\openrule
+         {\overline{\beta'^3_i},\Pred\,''^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
+         {s^3_i\OTarrow {\tau} s^3_{i+1}}\!\in\!\mathcal{T}\!\Bigg)  
+\end{mathpar}
+
+where\\
+\begin{mathpar} 
+s_1=s^1_0 \wedge s^1_{n_1+n_2}=s^2 \wedge s'^2 = s^3_0 \wedge s^3_{m_1+m_2}=s'\\
+\overline{\gamma}=\biguplus_{i=0}^{n_1+n_2} \vis{\overline{\beta'^1_i}} 
+\dotcup  \vis{\overline{\beta'^2}} \dotcup \biguplus_{i=0}^{m_1+m_2} \vis{\overline{\beta'^3_i}}
+\\
+\Pred=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred\,^2\subst{\Post_1}\land (\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2})\subst{\Post^1_i}
+\end{mathpar}
+
+\begin{mathpar}
 \forall i \in [0\ldots m_1].\openrule
@@
 \end{mathpar}
-where
-
+
+such that\\
 \begin{mathpar} 
@@
 
-and
-
-\begin{mathpar}
-\openrule
-         {
-           \overline{\gamma_2},\Pred_2,\Post_2  }
-         {s_1 \OTWeakarrow {\alpha} s_2} \in\! \WT
-
-\Rightarrow
-\Bigg(\forall i \in [0\ldots n_2].\openrule
-    {
-       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
-         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}  \wedge
-
-\openrule
-         {
-           \overline{\beta^2},\Pred^2,\Post^2 }
-         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
- \wedge
-\forall i \in [0\ldots m_2].\openrule
-         {
-           \overline{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
-         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
-\Bigg)         
-\end{mathpar}
-where\\
-\begin{mathpar} 
-s_1=s^1_0 \wedge s^1_n=s^2_0 \wedge s'^2 = s^3_0 \wedge s^3_{m_2}=s_2
-\\\\
-\overline{\gamma}=\biguplus_{i=0}^{n_2} \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^{m_2} \vis{\overline{\beta^3_i}}
-\\
-\Pred=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred^2\subst{\Post_1}\land (\bigwedge_{i=0}^{m_2}\Pred^3_i\subst{\Post^2})\subst{\Post^1_i}
-
-\end{mathpar}
+\end{itemize}
+\end{proof}
+
+------------------------------------------------------
 

### 2018-09-19 2016-Weak-FH-Bisim/WeakBisim.tex
change notations pNet ; P ; Q

@@
 \begin{definition}[pNets]\label{def-pnets}
-A pNet is a hierarchical structure where leaves are pLTSs and holes:\\
-$\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in 
+A pNet $\pNet$ is a hierarchical structure where leaves are pLTSs and holes:\\
+$\pNet,\pNetQ\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in 
 K}\myrangle$
@@
 
-The informal semantics of \pNet s is as follows.
-\pLTS s behave more or less like  classical automata with conditional branching and variables.
+The informal semantics of pNets is as follows.
+pLTSs behave more or less like  classical automata with conditional branching and variables.
 The actions on the \pLTS s can send or receive values, potentially modifying the value of variables.
-\pNet s are synchronisation entities: a \pNet composes several subnets and  synchronisation vectors define how the subnets interact, where a subnet is either a \pNet or a \pLTS.
-Synchronisation between subnets is defined by synchronisation vectors that express how an action of a subnet can be synchronised with actions of other subnet, and how the resulting synchronised action is visible to the outside of the \pNet.
+pNets are synchronisation entities: a pNet composes several subnets and  synchronisation vectors define how the subnets interact, where a subnet is either a pNet or a pLTS.
+Synchronisation between subnets is defined by synchronisation vectors that express how an action of a subnet can be synchronised with actions of other subnet, and how the resulting synchronised action is visible to the outside of the pNet.
 Synchronisation vectors also allow to explicitly export an action of a subnet to the next level, or to allow to subnets to synchronise and only exporting a non0observable action (provided such an non-visible action labels exist in the action algebra.
-Finally, a \pNet can leave subnets undefined and instead declare holes with a well-defined signature.
+Finally, a pNet can leave subnets undefined and instead declare holes with a well-defined signature.
 Holes can then be filled with a subnet.
@@
 	\overline{\symb{SV}}\myrangle$
- can be (partially) filled by providing  a pNets $\pNet'$ of the
+ can be (partially) filled by providing  a pNets $\pNetQ$ of the
 	right sort to fill one of  its holes.	
@@
 	%% \]
-	\[\pNet\left[\pNet'\right]_{j_0}= \mylangle 
-	\pNet_i^{i\in I}\uplus\{j_0\mapsto \pNet'\},\Sort_j^{j\in J\setminus \{j_0\}},
+	\[\pNet\left[\pNetQ\right]_{j_0}= \mylangle 
+	\pNet_i^{i\in I}\uplus\{j_0\mapsto \pNetQ\},\Sort_j^{j\in J\setminus \{j_0\}},
 	\overline{\symb{SV}}\myrangle
@@
 
-The semantics of open \pNet s will be defined  as an open automaton. An open
+The semantics of open pNets will be defined  as an open automaton. An open
 automaton is an automaton where each transition composes transitions of several LTSs with
@@
 
-  For any pNet: \pNet, let $\Leaves(\pNet) = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be 
+  For any pNet \pNet, let $\Leaves(\pNet) = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be 
   the set of pLTS at its leaves,
@@
 	\label{def:operationalSemantics}
-	The semantics of a pNet, $\pNet$ is an open automaton $A\!= 
+	The semantics of a pNet $\pNet$ is an open automaton $A\!= 
 	<\!\!Holes(\pNet),States(\pNet),InitState(\pNet),\mathcal{T}\!\!>$ where $\mathcal{T}$   is the smallest set of open transitions such that $\mathcal{T}=\{OT\,|\,\pNet \models OT \}$ and	$\pNet \models OT$	is defined by the following  rules:
@@
 As  our symbolic operational semantics provides an open automaton, we can apply the notion of
-	strong (symbolic) bisimulation on automata to open \pNet s:
-\begin{definition}[FH-bisimulation for open \pNet s]\label{def:bisim-pnets}
+	strong (symbolic) bisimulation on automata to open pNet s:
+\begin{definition}[FH-bisimulation for open pNets]\label{def:bisim-pnets}
 Two pNets are FH-bisimilar if there exist a relation between their associated 
@@
 \end{definition}
-We can now prove that \pNet\ composition  preserves
+We can now prove that pNet composition  preserves
 FH-bisimulation. More precisely, one can define two preservation
-properties, namely 1) when one hole of a \pNet\ is filled by two bisimilar other (open) pNets; and 2) when the same hole in two bisimilar pNets are
+properties, namely 1) when one hole of a pNet is filled by two bisimilar other (open) pNets; and 2) when the same hole in two bisimilar pNets are
 filled by the same pNet, in other words, composing a pNet with two
@@
 	\overline{\symb{SV}}\myrangle$.
-	Let $j_0\in J$ be a hole. Let $Q$ and $Q'$ be two FH-bisimilar pNets such that 
-	$\Sortop(Q)=\Sortop(Q')=\Sort_{j_0}$\footnote{Note that $\Sortop(Q)=\Sortop(Q')$ is 
+	Let $j_0\in J$ be a hole. Let $\pNetQ$ and $\pNetQ'$ be two FH-bisimilar pNets such that 
+	$\Sortop(\pNetQ)=\Sortop(\pNetQ')=\Sort_{j_0}$\footnote{Note that $\Sortop(\pNetQ)=\Sortop(\pNetQ')$ is 
 	ensured by 
 	strong bisimilarity.}. Then 
-	$\pNet[Q]_{j_0}$ and 
-	$\pNet[Q']_{j_0}$ are FH-bisimilar.
+	$\pNet[\pNetQ]_{j_0}$ and 
+	$\pNet[\pNetQ']_{j_0}$ are FH-bisimilar.
 \end{theorem}
@@
 	\overline{\symb{SV}}\myrangle$.
-	Let $j_0\in J$ be a hole. Let $Q$ and $Q'$ be two weak FH-bisimilar pNets such that 
-	$\Sortop(Q)=\Sortop(Q')=\Sort_{j_0}$\footnote{Note that $\Sortop(Q)=\Sortop(Q')$ is 
+	Let $j_0\in J$ be a hole. Let $\pNetQ$ and $Q'$ be two weak FH-bisimilar pNets such that 
+	$\Sortop(\pNetQ)=\Sortop(\pNetQ')=\Sort_{j_0}$\footnote{Note that $\Sortop(\pNetQ)=\Sortop(\pNetQ')$ is 
 	ensured by 
 	strong bisimilarity.}. Then 
-	$\pNet[Q]_{j_0}$ and 
-	$\pNet[Q']_{j_0}$ are weak FH-bisimilar.
+	$\pNet[\pNetQ]_{j_0}$ and 
+	$\pNet[\pNetQ']_{j_0}$ are weak FH-bisimilar.
 \end{theorem}
@@
 \begin{theorem}[Context equivalence for  weak bisimulation]\label{weak-thm-ctxt-eq}
-	Consider two weak FH-bisimilar open pNets:
+	Consider two  open pNets
 	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
@@
 	\Sort_j^{j\in 
-	J}, 	\overline{\symb{SV'}}\myrangle$ 
+	J}, 	\overline{\symb{SV'}}\myrangle$ that are weak FH-bisimilar
 	(recall they must have the same holes to be bisimilar).
-	Let $j_0\in J$ be a hole, and $Q$ be a pNet such that $\Sortop(Q)=\Sort_{j_0}$. Then 
-	$\pNet[Q]_{j_0}$ and 
-	$\pNet'[Q]_{j_0}$ are weak FH-bisimilar.
+	Let $j_0\in J$ be a hole, and $\pNetQ$ be a pNet such that $\Sortop(\pNetQ)=\Sort_{j_0}$. Then 
+	$\pNet[\pNetQ]_{j_0}$ and 
+	$\pNet'[\pNetQ]_{j_0}$ are weak FH-bisimilar.
 \end{theorem}

### 2018-09-19 2018-ModelCheckingPNets/checking.tex
formula and modal graph

@@
 
-An example of opM$\mu$ is the formula for open automaton in Sec.~\ref{Sec2:usecase}.  The formula can be expressed as follows:
+An example of opM$\mu$ is employed to the formula for open automaton in Sec.~\ref{Sec2:usecase}.  The formula can be expressed as follows:
 \begin{equation}\label{formula3}
-	\nu X(\langle fail?M\rangle\mu Y(M/t)(\langle resume\rangle X \vee \langle tick\rangle Y(t-1/t)\vee \langle ask\wedge reset\rangle true))
+	\langle fail?M\rangle \mu X(t).\langle finish\rangle true \vee (\langle reset\vee resume\rangle true \vee \langle tick\rangle X(t-1))
 \end{equation}
-First, a $fail$ occurs with receiving a value $M$, and then a $tick$ happens with decreasing $t$ by one.
-Or the system returns true after an $ask$ and the subsequent $reset$ occur.
-Otherwise, the system restarts after a $resume$ happens.
+
+If a $fail$ occurs with receiving a value $M$, and then a $finish$ happens only after a $resume$ or $reset$ occurs after $M$ times $tick happens$ with decreasing $t$ by one.
+The formula can be employed to express that an action $finish$ always eventually happens until the $reset$ or $resume$ occurs after the loop $tick$ happens.
+
+If we describe the Formula.~\ref{formula3} with a graphical pMG, it can be shown as Fig.~\ref{pmg3}:
+
+\begin{figure}
+\centering
+	\begin{tikzpicture}[->, shorten >=2pt, >=stealth, node distance=1.2cm,
+	noname/.style={ellipse, minimum width=1.5em, minimum height=1.5em, draw}]
+	\node[noname] (1)                                            				 	{$t_{1}$};
+	\node[noname] (2) [right=of 1]                               				 	{$t_{2}$};
+	\node[noname] (3) [right=of 2]                              				 	{$t_{3}$};
+	\node[noname] (4) [node distance=0.5cm and 2cm, above right=of 3]    {$t_{4}$};
+	\node[noname] (5) [right=of 4]                                					{$t_{5}$};
+	\node[noname] (6) [node distance=0.5cm and 1.8cm, below right=of 3]     {$t_{6}$};
+	\node[noname] (7) [node distance=0.4cm and 1.8cm, above right=of 6]     {$t_{7}$};
+	\node[noname] (8) [right=of 7]     {$t_{8}$};
+	\node[noname] (9) [node distance=0.4cm and 1.8cm, below right=of 6]     {$t_{9}$};
+
+	\path 	(1) edge                   	node[above] {} (2)
+	(2) edge                   	node[above] {} (3)
+	(3) edge 			node[above] {} (4)
+	(3) edge 			node[above] {} (6)
+	(9) edge[bend left]    node[below] {} (3)
+	(4) edge    		node[below] {} (5)
+	(6) edge    		node[below] {} (7)
+	(7) edge    		node[below] {} (8)
+	(6) edge    		node[below] {} (9);
+
+	\end{tikzpicture}
+	\caption{The associated pMG of Formula~\ref{formula3}}\label{pmg3}
+\end{figure}
+
+where:
+\begin{itemize}
+	\item $L_{N}(t_{1}) = (\{\}, \langle start?M\rangle, 1)$
+	\item $L_{N}(t_{2}) = (\{t\}, t := M, 1)$
+	\item $L_{N}(t_{3}) = (\{t\}, \vee, 1)$
+	\item $L_{N}(t_{4}) = (\{t\}, \langle finish\rangle, 1)$
+	\item $L_{N}(t_{5}) = (\{\}, true, 1)$
+	\item $L_{N}(t_{6}) = (\{t\}, \vee, 1)$
+	\item $L_{N}(t_{7}) = (\{t\}, \langle resume \vee reset\rangle, 1)$
+	\item $L_{N}(t_{8}) = (\{\}, true, 1)$
+	\item $L_{N}(t_{9}) = (\{t\}, \langle tick\rangle, 1)$
+\end{itemize}
+
+\NOTE{Explain the graph}
 
 \subsection{The modified algorithm}
+
+An open automaton is unfolded by a pNet with some pLTSs and holes.
+An open transition is defined by a hole action, a predicate, a postcondition, and a transition labelled by a synchronisation vector between a composition of states from different pLTSs.
+
+What we have to deal with in the algorithm is the $hole$ and $predicate$.
 

### 2018-09-20 2016-Weak-FH-Bisim/WeakBisim.tex
suite...
reunion a l i3s : preuve de decomposition WT -> T

@@
 	\overline{\symb{SV}}\myrangle$
- can be (partially) filled by providing  a pNets $\pNetQ$ of the
+ can be (partially) filled by providing  a pNet $\pNetQ$ of the
 	right sort to fill one of  its holes.	
@@
 
-This section defines the semantics of an open \pNet as a translation into an open automaton. 
+This section defines the semantics of an open pNet as a translation into an open automaton. 
 In this translation, the states of the open automata will be obtained from the states of the \pLTS s at the leaves of the composition.
@@
 \TODO{Ce paragraph a eu un probleme, je ne sais pas quand.... Vous avez une vieille version sous la main ?}
-This allows us to derive a bismulation theory for open \pNet s.
-As \pNet s are composition structures, it then makes sense to prove composition lemmas: we prove that the composition of bisimilar pNets are themselves bisimilar.
+This allows us to derive a bismulation theory for open pNets.
+As pNets are composition structures, it then makes sense to prove composition lemmas: we prove that the composition of bisimilar pNets are themselves bisimilar.
 
@@
 for a given pNet expression, we must have fresh local variables for
-each occurrence of a vector (= each time we instantiate rule
+each occurrence of a vector (i.e. each time we instantiate rule
 \TrDeux). Similarly the state variables of each copy of a
@@
 \end{mathpar}  
-
+\TODO{!!! FAUX -- to REMOVE}
 there exists  open transitions $\symb{OT} \in \mathcal{T}$:
@@
 
-\begin{lemma} Let $A = <J,\mathcal{S}, s_0,
+-\begin{lemma} Let $A = <J,\mathcal{S}, s_0,
     \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
@@
 \Bigg)        
-       \Longleftrightarrow\\  \Bigg( 
- \Big(\alpha = \tau \wedge  \vis{\overline{\beta^2}}=\emptyset \wedge \Pred\,^2 =\symb{True} \wedge \Post^2 =\symb{Id(s)}\Big) \Bigg) \bigvee  {
+       \bigvee\\   
+ \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\Big)  \Longleftrightarrow  {
 \openrule
@@
 
-\begin{proof} ($\Rightarrow$) We proceed by induction on the number of transitions $l$ with which we  build  a weak transition (introduced in Definition \ref{def:buildweakOT}), in particular we have  $l=n+m+1$.
+\begin{proof} ($\Rightarrow$) We proceed by induction on  $l=n+m+1$, which is in fact
+the number of transitions with which we  build  a weak transition (introduced in Definition \ref{def:buildweakOT}).
 \begin{itemize}
@@
 Induction step is to infer that formula holds for transitions of length $l + 1$.
-In particular, for $n+1$ or $m+1$, by adding the transition:
+As the condition holds for $l$, it means that there is $n$  $m$, $n'$,$m'$ such that $l=n+m+1$, and $l+1=n'+m'+1$ and either $n'=n+1$ or $m'=m+1$ (exclusively).
+We consider the case $n'=n+1$, $m'=m+1$ is similar. Side conditions are omitted for readability. We first focus on the left part of the disjunction
+Suppose
+$
+\Bigg(\forall i \in [0\ldots n+1].\openrule
+    {
+       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
+         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
+\quad
+\openrule
+         {
+           \overline{\beta^2},\Pred\,^2,\Post^2 }
+         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
+\quad \wedge\\
+\forall i \in [0\ldots m].\openrule
+         {
+           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
+         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
+\Bigg) $
+
+By recurrence hypothesis the theorem is true for any set of transitions of length $l$. In particular, we have
+
+\begin{mathpar}
+%\mprset {vskip=.5ex}
+%\inferrule 
+\Bigg(\forall i \in [0\ldots n].\openrule
+    {
+       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
+         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
+\quad
+\openrule
+         {
+           \overline{\beta^2},\Pred\,^2,\Post^2 }
+         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
+\quad \wedge\\
+\forall i \in [0\ldots m].\openrule
+         {
+           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
+         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
+\Bigg)        
+       \bigvee\\   
+ \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\Big)  \implies  {
+\openrule
+         {
+           \overline{\gamma},
+		\Pred, \Post
+				 } {s \OTWeakarrow {\alpha} s'} \in\WT
+}
+\end{mathpar}
+
+We need to prove the same implication with
+
+ by adding the transition:
 \begin{mathpar}
@@
 
-Second by using rule (3) \TODO{To complete}
+By rule (1) we have
+${ \openrule
+         {
+          \emptyset,True,Id(s')
+				 } {s' \OTWeakarrow {\tau} s'} \in \WT
+}$
+Finally by using rule (3) we compose the three rules:
+
+\TODO{todo}
+
+The right part of the disjunction, i.e.
+\begin{mathpar}
+\Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\Big)
+\end{mathpar}
+is handled trivially by rule (WT1)
 
 \end{itemize}
-\noindent ($\Leftarrow$) We proceed also  by induction on the number of transitions $l$ with which we  build  a weak transition.
+\TODO{add rule numbers WT1 WT2 WT3, and refer to them}
+
+\noindent ($\Leftarrow$) We proceed by structural induction on the rules  building  the weak transition.
 
 \begin{itemize}
-\item Basis: suppose that $\OTWeakarrow {\alpha}$ cannot be subdivided. So for a given weak transition:
-
-\begin{mathpar}
-{ \openrule
-         {
-           \overline{\gamma}\!,\Pred,\Post
-				 } {s \OTWeakarrow {\alpha} s'} \in \WT
-}
-\end{mathpar}
-We have two cases:
-\begin{itemize}
-\item either $\alpha = \tau$, $s=s'$, $\overline{\beta}=\emptyset$, $\Pred = \symb{True}$ and $\Post=\symb{Id}(s)$. So by rule (2) we have: 
+\item case rule (WT1):
 \begin{mathpar}
@@
 \end{mathpar}
-\item Otherwise, by rule (2) we conclude that we have: 
+In this case we can directly conclude by the right part of the disjunction.
+
+\item case rule (WT2). \TODO{write inference}
 \begin{mathpar}
@@
 \end{mathpar}
+
+This proves the implication with $n=0$ and $m=0$.
+
+\item case rule (WT3).
+\TODO{put WT3 here}
+
+%
+%
+%Basis: suppose that $\OTWeakarrow {\alpha}$ cannot be subdivided. So for a given weak transition:
+%
+%\begin{mathpar}
+%{ \openrule
+%         {
+%           \overline{\gamma}\!,\Pred,\Post
+%				 } {s \OTWeakarrow {\alpha} s'} \in \WT
+%}
+%\end{mathpar}
+%We have two cases:
+%\begin{itemize}
+\item either $\alpha = \tau$, $s=s'$, $\overline{\beta}=\emptyset$, $\Pred = \symb{True}$ and $\Post=\symb{Id}(s)$. So by rule (2) we have:
+
+\item Otherwise, by rule (2) we conclude that we have:
+
 where $\overline{\gamma} = \vis{\overline{\beta}}$
@@
     {
-       \overline{\beta'^1_i},\Pred\,'^1_i,\Post'^1_i   }
+       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
          {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}  \wedge
@@
          {
-           \overline{\beta'^2},\Pred\,'^2,\Post'^2 }
+           \overline{\beta^2},\Pred^2,\Post^2 }
          {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
@@
          {
-           \overline{\beta'^3_i},\Pred\,'^3_i,({x^3_k\gets e^3_k})^{k\in K'}    }
+           \overline{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
          {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
@@
 s_1=s^1_0 \wedge s^1_n=s^2_0 \wedge s'^2 = s^3_0 \wedge s^3_{m_2}=s_2,
-\overline{\gamma_2}=\biguplus_{i=0}^{n_2} \vis{\overline{\beta'^1_i}} \dotcup  \vis{\overline{\beta'^2}} \dotcup \biguplus_{i=0}^{m_2} \vis{\overline{\beta'^3_i}}
+\overline{\gamma_2}=\biguplus_{i=0}^{n_2} \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^{m_2} \vis{\overline{\beta^3_i}}
 \\
-\Pred_2=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred\,^2\subst{\Post_1}\land (\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2})\subst{\Post^1_i}
-
+\Pred_2=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred\,^2\subst{ \biguplus_{i=0}^{n_2}\Post^1_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^1_i}
+\\
+\Post_2= ({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\biguplus_{i=0}^{n_2} \Post^1_i}})^{k\in K}
 \end{mathpar}
@@
 }\bigg)
-\!\Rightarrow\!
-\Bigg(\!\forall i\! \in\! [0\ldots(n_1\!+\!n_2)].\openrule
-    {
-       \overline{\beta'^1_i},\Pred\,''^1_i,\Post''^1_i   }
-         {s^1_i \OTarrow {\tau} s^1_{i+1}}\! \in\!\mathcal{T} \wedge
+ \Rightarrow
+\Bigg(\forall i\in [0\ldots(n_1\!+\!n_2)].\openrule
+    {
+       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
+         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in\mathcal{T} \wedge
 
@@
          {
-           \overline{\beta'^2},\Pred\,''^2,\Post''^2 }
-         {s^2 \OTarrow {\alpha} s'^2}\! \in\! \mathcal{T}
-\!\wedge
-\forall i\! \in\! [0\ldots(m_1\!+\!m_2)].\openrule
-         {\overline{\beta'^3_i},\Pred\,''^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
-         {s^3_i\OTarrow {\tau} s^3_{i+1}}\!\in\!\mathcal{T}\!\Bigg)  
+           \overline{\beta^2},\Pred^2,\Post^2 }
+         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
+\wedge
+\forall i \in [0\ldots(m_1\!+\!m_2)].\openrule
+         {\overline{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
+         {s^3_i\OTarrow {\tau} s^3_{i+1}}\in\mathcal{T}\Bigg)  
 \end{mathpar}
@@
 s_1=s^1_0 \wedge s^1_{n_1+n_2}=s^2 \wedge s'^2 = s^3_0 \wedge s^3_{m_1+m_2}=s'\\
-\overline{\gamma}=\biguplus_{i=0}^{n_1+n_2} \vis{\overline{\beta'^1_i}} 
-\dotcup  \vis{\overline{\beta'^2}} \dotcup \biguplus_{i=0}^{m_1+m_2} \vis{\overline{\beta'^3_i}}
+\overline{\gamma}=\biguplus_{i=0}^{n_1+n_2} \vis{\overline{\beta^1_i}} 
+\dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^{m_1+m_2} \vis{\overline{\beta^3_i}}
 \\
-\Pred=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred\,^2\subst{\Post_1}\land (\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2})\subst{\Post^1_i}
+\Pred=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred\,^2\subst{ \biguplus_{i=0}^{n_2}\Post^1_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^1_i}
+\\
+\Post= ({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\biguplus_{i=0}^{n_2} \Post^1_i}})^{k\in K}
 \end{mathpar}
 
-\begin{mathpar}
-\forall i \in [0\ldots m_1].\openrule
-    {
-       \overline{\beta^3_i},\Pred^3_i,\Post^3_i   }
-         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}         
-\end{mathpar}
-
-such that\\
-\begin{mathpar} 
-s_2=s^3_0 \wedge s^1_{m_1}=s' \quad
-\overline{\gamma_3}=\biguplus_{i=0}^{m_1} \vis{\overline{\beta^3_i}} 
-\quad
-\Pred_3=\bigwedge_{i=0}^{m_1}\Pred^3_i\quad \Post_3= \biguplus_{i=0}^{m_1} \Post_i^3
-\end{mathpar}
-
-\end{itemize}
 \end{proof}
-
-------------------------------------------------------
+-----------------------------------------------------
 

### 2018-09-20 2016-Weak-FH-Bisim/WeakBisim.tex
WT1, WT2, WT3

@@
   between INRIA and ECNU, Shanghai}}
-\author{ Ludovic Henrio\inst{1}  \ \ \  Eric Madelaine\inst{1,2} \ \ \ Rab\'ea}
+\author{Ludovic Henrio\inst{1}  \ \ \  Eric Madelaine\inst{1,2} \ \ \ Rab\'ea}
 \institute{Univ. of Nice Sophia Antipolis, CNRS, UMR 7271, 06900 Sophia Antipolis, France
@@
   Let $A = <J,\mathcal{S},s_0,\mathcal{T}>$ be an open automaton. 
-The weak open automaton \emph{derived} from $A$ is an open automaton  $<J,\mathcal{S},s_0,\WT>$ where $\WT$ is derived from $\mathcal{T}$ as follows
+The weak open automaton \emph{derived} from $A$ is an open automaton  $<J,\mathcal{S},s_0,\WT>$ where $\WT$ is derived from $\mathcal{T}$ as follows:
 
@@
            \emptyset,\symb{True},Id(s)}
-         {s \OTWeakarrow {\tau} s} \in \WT
+         {s \OTWeakarrow {\tau} s} \in \WT  \qquad \WTUn
  \end{mathpar}
@@
 				 } {s \OTWeakarrow {\alpha} s'} \in \WT
-}
+}\qquad \WTDeux
 %\inferrule{
@@
          {s \OTWeakarrow {\alpha} s'} \in\WT
-}
+} \WTTrois
 \end{mathpar}

### 2018-09-20 2016-Weak-FH-Bisim/WeakBisim.tex
use \True et \Id #8

--- 2018-09-20 2016-Weak-FH-Bisim/WeakBisim.tex
@@
       if $\Pred_{s,t}$       is 
-      true, i.e. the states are related when the variables in $s$ and $t$ verify the 
+      t\\True, i.e. the states are related when the variables in $s$ and $t$ verify the 
       predicate $\Pred_{s,t}$.
@@
      $  OT_2  = \openrule{
-      \emptyset; Pred=true;  \\ Post=\{m_1\_m:=s_1\_m, m_1\_b:=s_1\_sb, s_2\_sb:=s_1\_sb\}
+      \emptyset; Pred=\True;  \\ Post=\{m_1\_m:=s_1\_m, m_1\_b:=s_1\_sb, s_2\_sb:=s_1\_sb\}
                       }
@@
 automata that is an FH-bisimulation and their initial states are in the relation, i.e. 
-the predicate associated to the relation between the initial states is true.
+the predicate associated to the relation between the initial states is \True.
 \end{definition}
@@
          {
-           (j\mapsto\tau),\symb{True},\symb{Id}(s)}
+           (j\mapsto\tau),\True,\Id(s)}
          {s \OTarrow {\tau} s}
@@
          {s \OTarrow {\alpha} s'}
-         \in \mathcal{T} \] we have \[ \alpha=\tau\land s=s'\land \Post=\symb{Id}(s)
+         \in \mathcal{T} \] we have \[ \alpha=\tau\land s=s'\land \Post=\Id(s)
 \]
@@
          {
-           \emptyset,\symb{True},Id(s)}
+           \emptyset,\True,\Id(s)}
          {s \OTWeakarrow {\tau} s} \in \WT
@@
 automata that is a Weak FH-bisimulation and their initial states are in the relation, i.e. 
-the predicate associated to the relation between the initial states is true.
+the predicate associated to the relation between the initial states is \True.
  \end{definition}
@@
 A pNet $\mylangle \pNet_i^{i\in I} , \Sort_j^{j\in J}, \overline{\symb{SV}}\myrangle$
- \emph{cannot observe silent actions} if it verifies:\\ $\forall i\in I\uplus J.\, \SV{(i\mapsto \tau)}{\tau}{\symb{True}}\in \overline{\symb{SV}}$ and $\forall SV_k\in \overline{\symb{SV}}, \forall i,j\in I_k\uplus J_k.\,i\neq j \Rightarrow \alpha'_k\neq\tau$
+ \emph{cannot observe silent actions} if it verifies:\\ $\forall i\in I\uplus J.\, \SV{(i\mapsto \tau)}{\tau}{\True}\in \overline{\symb{SV}}$ and $\forall SV_k\in \overline{\symb{SV}}, \forall i,j\in I_k\uplus J_k.\,i\neq j \Rightarrow \alpha'_k\neq\tau$
 \end{definition}
@@
      $  \openrule{
-      \emptyset; Pred=true; Post=\{m_1\_m:=s_1\_m, m_1\_b:=s_1\_sb, s_2\_sb:=s_1\_sb\}
+      \emptyset; Pred=\True; Post=\{m_1\_m:=s_1\_m, m_1\_b:=s_1\_sb, s_2\_sb:=s_1\_sb\}
                       }
@@
      $  \openrule{
-  \emptyset; Pred=true; Post=r_2\_b:=r_1\_b; s_2\_b:=s_1\_b   \}
+  \emptyset; Pred=\True; Post=r_2\_b:=r_1\_b; s_2\_b:=s_1\_b   \}
                       }
@@
 Where $j_0\in I_1$ or $j_0\in I_2$
-We know each premise is true for $P[Q]_{j_0}$ and try to prove the equivalent premise for 
+We know each premise is \True for $P[Q]_{j_0}$ and try to prove the equivalent premise for 
 $P$. 
@@
 Definition~\ref{def:operationalSemantics}). 
-We know each premise is true for $P$ and try to prove the equivalent premise for 
+We know each premise is \True for $P$ and try to prove the equivalent premise for 
 $P[Q]_{j_0}$ (using the open transition of $Q$). 
@@
 
-By recurrence hypothesis the theorem is true for any set of transitions of length $l$. In particular, we have
+By recurrence hypothesis the theorem is \True for any set of transitions of length $l$. In particular, we have
 
@@
          {
-          \emptyset,True,Id(s')
+          \emptyset,\True,\Id(s')
 				 } {s' \OTWeakarrow {\tau} s'} \in \WT
@@
          {
-           \emptyset,\symb{True},\symb{Id}(s)
+           \emptyset,\True,\Id(s)
 				 } {s \OTarrow {\tau} s} \in \mathcal{T}
@@
 %\begin{itemize}
-\item either $\alpha = \tau$, $s=s'$, $\overline{\beta}=\emptyset$, $\Pred = \symb{True}$ and $\Post=\symb{Id}(s)$. So by rule (2) we have:
+\item either $\alpha = \tau$, $s=s'$, $\overline{\beta}=\emptyset$, $\Pred = \True$ and $\Post=\Id(s)$. So by rule (2) we have:
 
@@
       {\inferrule*
-        {0 \xrightarrow{ium(?tgt2_2), True, \emptyset}_{gw2} 2}
+        {0 \xrightarrow{ium(?tgt2_2), \True, \emptyset}_{gw2} 2}
         {\sm{gw2} \models
@@
           \openrule
-              {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad \sm{True}}
+              {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad \True}
               {\ostate{0} \OTarrow{im(?tgt1_1)} \ostate{1}}
@@
       \phi'\!=\!\phi\!+\!\{x'_i\!\to\!V_i|x'_i\!\in\!\iv(\alpha)\land V_i\!\in\!\mathcal{D}\} \\
-      e_b\phi'\!=\!\symb{True} \\ \phi''\!=\!\phi'+\{x_j\!\to\! e_j\phi'|j\!\in\! J\}}
+      e_b\phi'\!=\!\True \\ \phi''\!=\!\phi'+\{x_j\!\to\! e_j\phi'|j\!\in\! J\}}
     {(s,\phi) \xrightarrow{\alpha\phi'} (s',\phi'') \in\llbracket\mylangle S,s_0,

### 2018-09-20 2016-Weak-FH-Bisim/WeakBisim.tex

@@
          {
-           \emptyset,\True,\Id(s)}
-         {s \OTWeakarrow {\tau} s} \in \WT
+           \emptyset,\symb{True},\Id(s)}
+         {s \OTWeakarrow {\tau} s} \in \WT  \qquad \WTUn
  \end{mathpar}

### 2018-09-24 2016-Weak-FH-Bisim/WeakBisim.tex
Proof improvement
Proof Lemma 4 completed

@@
 
--\begin{lemma} Let $A = <J,\mathcal{S}, s_0,
+\begin{lemma} Let $A = <J,\mathcal{S}, s_0,
     \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
@@
 \end{mathpar} 
-by rule (2) we directly conclude 
+by rule (\WTDeux) we directly conclude 
  \begin{mathpar}
@@
 %}
+
+\openrule
+         {
+           \overline{\beta},\Pred,\Post}
+         {s \OTarrow {\alpha} s'} \in \mathcal{T} \implies 
 { \openrule
@@
 As the condition holds for $l$, it means that there is $n$  $m$, $n'$,$m'$ such that $l=n+m+1$, and $l+1=n'+m'+1$ and either $n'=n+1$ or $m'=m+1$ (exclusively).
-We consider the case $n'=n+1$, $m'=m+1$ is similar. Side conditions are omitted for readability. We first focus on the left part of the disjunction
-Suppose
-$
+We consider the case $n'=n+1$, $m'=m+1$ is similar. Side conditions are omitted for readability. We first focus on the left part of the disjunction. Suppose we have:
+\begin{mathpar}
 \Bigg(\forall i \in [0\ldots n+1].\openrule
@@
          {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
-\Bigg) $
-
-By recurrence hypothesis the theorem is \True for any set of transitions of length $l$. In particular, we have
+\Bigg) 
+\end{mathpar}
+
+By recurrence hypothesis the theorem is \True~ for any set of transitions of length $l$. In particular, we have
 
@@
 		\Pred, \Post
-				 } {s \OTWeakarrow {\alpha} s'} \in\WT
+				 } {s' \OTWeakarrow {\alpha} s''} \in\WT
 }
@@
 
-We need to prove the same implication with
-
- by adding the transition:
+We need to prove the same implication with  by adding the transition:
 \begin{mathpar}
@@
 \end{mathpar}
-
-First by using rule (2) we can directly conclude :
+It will remain so. First by using rule (\WTDeux) we can directly conclude :
 \begin{mathpar}
- % \mprset {vskip=.5ex}
-%\inferrule{
-% \openrule
-%         {
-%           \overline{\beta},\Pred,\Post}
-%         {s \OTarrow {\tau} s'} \in \mathcal{T}
-%}
+
+ \openrule
+         {
+           \overline{\beta},\Pred,\Post}
+         {s \OTarrow {\tau} s'} \in \mathcal{T}
+\implies 
 { \openrule
@@
 
-By rule (1) we have
-${ \openrule
+On the other hand, by rule (\WTUn) we have
+\begin{mathpar}
+ \openrule
          {
           \emptyset,\True,\Id(s')
-				 } {s' \OTWeakarrow {\tau} s'} \in \WT
-}$
-Finally by using rule (3) we compose the three rules:
-
-\TODO{todo}
+				 } {s'' \OTWeakarrow {\tau} s''} \in \WT
+\end{mathpar}
+
+Finally by using rule (\WTTrois) we compose the three weak transitions:
+
+\begin{mathpar}
+  \mprset {vskip=.5ex}
+\inferrule {\openrule
+         {
+           \vis{\overline{\beta}},\Pred,\Post   }
+         {s \OTWeakarrow {\tau} s'} \in \WT
+\qquad
+\openrule
+         {
+           \overline{\gamma},
+		\Pred, \Post
+				 } {s' \OTWeakarrow {\alpha} s''} \in\WT
+\qquad
+\openrule
+         {
+          \emptyset,\True,\Id(s')
+				 } {s'' \OTWeakarrow {\tau} s''} \in \WT
+\\
+\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
+}
+{
+\openrule
+         {
+          \vis{\overline{\beta}} \dotcup \overline{\gamma},
+		\Pred,
+				({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K} } 
+         {s \OTWeakarrow {\alpha} s''} \in\WT
+} \WTTrois
+\end{mathpar}
 
@@
 \end{mathpar}
-is handled trivially by rule (WT1)
+is handled trivially by rule (\WTUn)
 
 \end{itemize}
-\TODO{add rule numbers WT1 WT2 WT3, and refer to them}
 
@@
 \begin{itemize}
-\item case rule (WT1):
+\item Case rule (\WTUn):
 \begin{mathpar}
@@
            \emptyset,\True,\Id(s)
-				 } {s \OTarrow {\tau} s} \in \mathcal{T}
+				 } {s \OTWeakarrow {\tau} s} \in \WT
 }
@@
 In this case we can directly conclude by the right part of the disjunction.
-
-\item case rule (WT2). \TODO{write inference}
+\begin{mathpar}
+{ \openrule
+         {
+           \emptyset,\True,\Id(s)
+				 } {s \OTWeakarrow {\tau} s} \in \WT
+} \implies \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\Big)
+\end{mathpar}
+
+\item Case rule (\WTDeux):
 \begin{mathpar}
@@
          {
+           \overline{\gamma},\Pred,\Post}
+         {s \OTWeakarrow {\alpha} s'} \in \WT \implies
+         \openrule
+         {
            \overline{\beta},\Pred,\Post}
-         {s \OTarrow {\alpha} s'} \in \mathcal{T}
+         {s \OTWeakarrow {\alpha} s'} \in \mathcal{T}         
 \end{mathpar}
-
-This proves the implication with $n=0$ and $m=0$.
-
-\item case rule (WT3).
-\TODO{put WT3 here}
-
-%
-%
-%Basis: suppose that $\OTWeakarrow {\alpha}$ cannot be subdivided. So for a given weak transition:
-%
-%\begin{mathpar}
-%{ \openrule
-%         {
-%           \overline{\gamma}\!,\Pred,\Post
-%				 } {s \OTWeakarrow {\alpha} s'} \in \WT
-%}
-%\end{mathpar}
-%We have two cases:
-%\begin{itemize}
-\item either $\alpha = \tau$, $s=s'$, $\overline{\beta}=\emptyset$, $\Pred = \True$ and $\Post=\Id(s)$. So by rule (2) we have:
-
-\item Otherwise, by rule (2) we conclude that we have:
-
-where $\overline{\gamma} = \vis{\overline{\beta}}$
-\end{itemize}
-\item Step: by using rule (3) we can rewrite a weak transition:
-
+where $\overline{\gamma} = \vis{\overline{\beta}}$.
+These two cases prove the implication with $n=0$ and $m=0$.
+
+\item Case rule (\WTTrois):
 \begin{mathpar}
-{ \openrule
-         {
-           \overline{\gamma}\!,\Pred,\Post
-				 } {s \OTWeakarrow {\alpha} s'} \in \WT
+  \mprset {vskip=.5ex}
+\inferrule {\openrule
+         {
+           \overline{\gamma_1},\Pred_1,\Post_1   }
+         {s \OTWeakarrow {\tau} s_1} \in \WT
+\qquad
+\openrule
+         {
+           \overline{\gamma_2},\Pred_2,\Post_2  }
+         {s_1 \OTWeakarrow {\alpha} s_2} \in \WT
+\qquad
+\openrule
+         {
+           \overline{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
+         {s_2 \OTWeakarrow {\tau} s'} \in\WT
+\\
+\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
+}
+{
+\openrule
+         {
+           \overline{\gamma_1}\dotcup \overline{\gamma_2}\dotcup\overline{\gamma_3},
+		\Pred,
+				({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K} } 
+         {s \OTWeakarrow {\alpha} s'} \in\WT
 }
@@
 
-as
-
-\begin{mathpar}
-\inferrule{
-\openrule
-         {
-           \overline{\gamma_1},\Pred_1,\Post_1   }
-         {s \OTWeakarrow {\tau} s_1} \in\! \WT
-\quad
-\openrule
-         {
-           \overline{\gamma_2},\Pred_2,\Post_2  }
-         {s_1 \OTWeakarrow {\alpha} s_2} \in\! \WT
-\quad
-\openrule
-         {
-           \overline{\gamma_3},\Pred_3,\Post_3 }
-         {s_2 \OTWeakarrow {\tau} s'} \in\!\WT
-%\\
-%\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
-}{}
-\end{mathpar}
-
-such that \\
-$\overline{\gamma}=\overline{\gamma_1} \dotcup \overline{\gamma_2} \dotcup \overline{\gamma_3}$, 
-$\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}$, and $\Post=$ \TODO{Voir comment l'exprimer}\\
+%where 
+%$\overline{\gamma}=\overline{\gamma_1} \dotcup \overline{\gamma_2} \dotcup \overline{\gamma_3}$,
+%$\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}$, and $\Post= ({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K}$
 
@@
 
-\item By induction hypothesis and simplification we have: 
+\item By induction hypothesis this means each tau weak transition can be written as a series of tau transitions, hence by simplification we have: 
 \begin{mathpar}
@@
 \end{mathpar}
-where 
-\begin{mathpar} 
-s=s^1_0 \wedge\, s^1_{n_1}=s_1 \quad
-\overline{\gamma_1}=\biguplus_{i=0}^{n_1} \vis{\overline{\beta^1_i}} 
-\quad
-\Pred_1=\bigwedge_{i=0}^{n_1}\Pred^1_i\quad \Post_1= \biguplus_{i=0}^{n_1} \Post_i^1
-\end{mathpar}
-
-\item and
+where \\
+$
+s=s^1_0 \wedge s^1_{n_1}\!=s_1,
+\overline{\gamma_1}=\biguplus_{i=0}^{n_1} \vis{\overline{\beta^1_i}}, 
+\Pred_1\!=\!\bigwedge_{i=0}^{n_1}\Pred^1_i, \Post_1= \biguplus_{i=0}^{n_1} \Post_i^1\\
+$
+
+\item Similarly, we have: 
 \begin{mathpar}
@@
 \end{mathpar}
-where
-\begin{mathpar} 
-s_2=s^3_0 \wedge s^1_{m_1}=s'\quad
-\overline{\gamma_3}=\biguplus_{i=0}^{m_1} \vis{\overline{\beta^3_i}}\quad
-\Pred_3\!=\!\bigwedge_{i=0}^{m_1}\Pred^3_i \quad \Post_3= \biguplus_{i=0}^{m_1} \Post_i^3
-\end{mathpar}
-
-\item and 
+where\\
+$
+s_2=s^3_0 \wedge s^1_{m_1}=s',
+\overline{\gamma_3}=\biguplus_{i=0}^{m_1} \vis{\overline{\beta^3_i}},
+\Pred_3\!=\!\bigwedge_{i=0}^{m_1}\Pred^3_i,\Post_3\!=\! \biguplus_{i=0}^{m_1} \Post_i^3\\
+$
+
+\item On the other hand, by induction hypothesis we have:
 \begin{mathpar}
@@
 where\\
-\begin{mathpar} 
+$
 s_1=s^1_0 \wedge s^1_n=s^2_0 \wedge s'^2 = s^3_0 \wedge s^3_{m_2}=s_2,
@@
 \Post_2= ({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\biguplus_{i=0}^{n_2} \Post^1_i}})^{k\in K}
-\end{mathpar}
+$
 \end{enumerate}
-
-Therefore, we can conclude that:
+~~\\
+
+Therefore, we can deduce that:
 \begin{mathpar}
@@
 where\\
-\begin{mathpar} 
-s_1=s^1_0 \wedge s^1_{n_1+n_2}=s^2 \wedge s'^2 = s^3_0 \wedge s^3_{m_1+m_2}=s'\\
+$
+s_1\!=\!s^1_0 \wedge s^1_{n_1+n_2}\!=s^2 \wedge s'^2 = s^3_0 \wedge s^3_{m_1+m_2}\!=\!s',
 \overline{\gamma}=\biguplus_{i=0}^{n_1+n_2} \vis{\overline{\beta^1_i}} 
@@
 \Post= ({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\biguplus_{i=0}^{n_2} \Post^1_i}})^{k\in K}
-\end{mathpar}
+$
+
+\end{itemize}
 

### 2018-09-24 2016-Weak-FH-Bisim/WeakBisim.tex
A bit of text and organisation

--- 2018-09-20 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 This section defines the semantics of an open pNet as a translation into an open automaton. 
-In this translation, the states of the open automata will be obtained from the states of the \pLTS s at the leaves of the composition.
-The predicates on the transition will be obtained both from the predicates on the \pLTS s transitions and from the
-\TODO{Ce paragraph a eu un probleme, je ne sais pas quand.... Vous avez une vieille version sous la main ?}
-This allows us to derive a bismulation theory for open pNets.
-As pNets are composition structures, it then makes sense to prove composition lemmas: we prove that the composition of bisimilar pNets are themselves bisimilar.
-
-%
+In this translation, the states of the open automata are obtained from the states of the pLTSs at the leaves of the composition.
+The predicates on the transition is obtained both from the predicates on the pLTSs transitions and from the synchronisation vectors involved in the transition.
+
+The definition of bisimulation for open automata allows us to derive a bismulation theory for open pNets.
+As pNets are composition structures, it then makes sense to prove composition lemmas: we prove that the composition of strongly bisimilar pNets are themselves bisimilar.
+
+\subsection{Deriving an open automaton from an open pNet}
+To derive an open automaton from a pNet, we need to describe the set of states of the automaton, and then we will detail the construction rule for transitions of the automaton, this will rely on the derivation of predicate unifying synchronisation vectors and the actions of the pNets involved in a given synchronisation.
+
 %Then the semantics of a pNet is characterized by a set of {\em open
@@
 
-We define states of open pNets as tuples of states. We denote them
+We define first states of open pNets as tuples of states. We denote them
  as $\triangleleft\ldots\triangleright$ for distinguishing tuple 
@@
 predicate $\Predsv$ is not satisfiable, then the transition associated with the 
-synchronisation will not occur in the considered state.
-
-In any other case (if the action families do not match or if there is no valuation of
-variables such that the above formula can be ensured) the predicate is undefined.
-
-This definition is not constructive but it is easy to build the predicate constructively
-by brute-force unification of the sub-pNets
-actions with the corresponding vector actions, possibly followed by a simplification
-step.
+synchronisation will not occur in the considered state, or will occur with a \False\ precondition which is equivalent.
+If the action families do not match or if there is no valuation of
+variables such that the above formula can be ensured the predicate is undefined.
+
+The definition of this predicate is not constructive but it is easy to build the predicate constructively by brute-force unification of the sub-pNets actions with the corresponding vector actions, possibly followed by a simplification step.
 
@@
 
-We build the semantics of open pNets as an open automaton where LTSs are the pLTSs at
-the leaves of the pNet structure, and the states are given by 
+We build the semantics of open pNets as an open automaton over the states  given by 
 Definition~\ref{def-states}. The open transitions first
@@
 	%%include it, because it may change the decidability conditions on predicates}
-
+\end{definition}
         	A key to understand this rule is that the open transitions are
@@
 
-\end{definition}
-%
-
+Note that  the construction is symbolic, and each open-transition deduced expresses a whole family of
+behaviours, for any possible values of the variables.
+%
+
+\LUDO{Je sais pas de quoi parle le prochain todo :-( l'exemple?}
 \TODO{Ceci n'est pas nouveau, n'est-ce pas, est-ce utile pour le lecteur ici ? Ou est-ce qu'on bouge tous ces ``details techniques'' dans une annexe ? Si oui, je refais avec un morceau de ABP}
@@
 
-Note that while the scenario above is expressed as a single
-instantiation of the possible behaviours, the constructions below are
-kept symbolic, and each open-transition deduced expresses a whole family of
-behaviours, for any possible values of the variables.
-
 \paragraph{Variable management.}
@@
 As  our symbolic operational semantics provides an open automaton, we can apply the notion of
-	strong (symbolic) bisimulation on automata to open pNet s:
+	strong (symbolic) bisimulation on automata to open pNets:
 \begin{definition}[FH-bisimulation for open pNets]\label{def:bisim-pnets}
@@
 bisimilar contexts. The general case will be obtained by
-transitivity of the bisimulation relation.
+transitivity of the bisimulation relation (Theorem~\ref{thm-equiv}).
 
@@
 \end{theorem}
-%
-%In the following we use $\approx$ to denote equality modulo alpha conversion of free 
-%variables. In practice, $x\approx y$ can be obtained if: $x=clone(a) \land y=clone(a)$.
+This theorem is quite powerful somehow states that the theory of open pNets is convenient to study properties of process composition.
+Open pNets can indeed be used to study process operators and process algebras, as shown in~\cite{henrio:Forte2016}, or to study interaction protocols \TODO{ref vers ABP?}
 

### 2018-09-24 2016-Weak-FH-Bisim/WeakBisim.tex
Intro weak bisim

@@
 actions of other systems in its environment.
+We show here that under such assumption of non-observability of internal actions, we can define a weak bisimulation relation that is compositional, in the sense of open pNet composition.
+In this section we will first define a notion of weak transition similar to open transition.
+In fact a weak open transition is made of several open transitions labelled as internal transitions, plus potentially one non-internal open transition.
+This allows us to define weak open automata, and a weak bisimulation relation based on these weak open automata.
+Finally, we apply this weak bisimulation to open pNets, obtain a weak bisimilarity relationship for open pNets, and prove that this relation has compositional properties.
 

### 2018-09-24 2016-Weak-FH-Bisim/WeakBisim.tex
notes de reu

@@
 \section*{Status and TODO list}
+Notes de reunion 24 Sept
+
+- on remet l exemple de enable, etendu pour weak (Eric)
+
+- reste nos 5 thm a prouver: transitivite, decomposition/ recomposition, congruence x 2
+
+- etat de l art: il faudrait des refs sur bisim en gemneral, probablement avec pas mal de pi calcul (Eric?), des refs sur pourquoi pnets et des refs sur utilite de la weak bisim en verif
+
+- target SIAvocs ou SCP ou JLamp
+
 Conventions
@@
 
-\paragraph{Related works}
-
-\TODO{TODO ... or rather a dedicated section}
-
 \paragraph{Structure}
@@
 Finally, Section~\ref{section:conclusion} concludes the paper.
+
+\section{Related works}
+
+\TODO{TODO ... }
 
@@
        \bigvee\\   
- \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\Big)  \Longleftrightarrow  {
+ \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)  \Longleftrightarrow  {
 \openrule

### 2018-09-24 2016-Weak-FH-Bisim/WeakBisim.tex
minor changes

--- 2018-09-24 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 where\\
-\begin{mathpar} 
+$
 s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s', \quad
@@
 \Post=({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K}
-\end{mathpar}
+$
 
@@
 
-\item By induction hypothesis this means each tau weak transition can be written as a series of tau transitions, hence by simplification we have: 
+\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau transitions such $n_1=n+m+1$, hence by simplification we have: 
 \begin{mathpar}

### 2018-09-27 2016-Weak-FH-Bisim/WeakBisim.tex
lemma 4: notations
reu rabea: symbols
changes
corollaire: weak FH-bisim

@@
 \section*{Status and TODO list}
+
 Notes de reunion 24 Sept
@@
          {s \OTarrow {\alpha} s'}
-         \in \mathcal{T} \] we have \[ \alpha=\tau\land s=s'\land \Post=\Id(s)
+         \in \mathcal{T} \] we have \[ \alpha=\tau\land s=s'\land \Pred=\True\land\Post=\Id(s)
 \]
@@
 
-Two pNets are Weak FH-bisimilar if there exist a relation between their associated 
+Two pNets are weak FH-bisimilar if there exist a relation between their associated 
 automata that is a Weak FH-bisimulation and their initial states are in the relation, i.e. 
@@
 
-\begin{lemma} Let $A_1 = <J,\mathcal{S}_1, s_0,
-    \mathcal{T}_1>$ be open automata and $<J,\mathcal{S}_1, s_0,
-    \WT_1>$ be the
-weak open automata derived from $A_1$.
-
-\begin{itemize}
- \item  For any weak open transition $\symb{WOT} \in \WT$:
- \begin{mathpar}
-     \openrule
-         {
-           \gamma_j^{j\in J},\Pred_{OT},\Post_{OT}}
-         {s \OTWeakarrow {\alpha} s'}
-
-\end{mathpar}  
-\TODO{!!! FAUX -- to REMOVE}
-there exists  open transitions $\symb{OT} \in \mathcal{T}$:
-
-\begin{mathpar}
-     \openrule
-         {
-           \beta_j^{j\in J},\Pred_{OT},\Post_{OT}}
-         {s \OTarrow {\alpha} s'}
-
-\end{mathpar}
- or $s=s'$ and $\alpha = \tau$
-\end{itemize}
-
-\begin{proof} 
-We can rewrite $s \OTWeakarrow {} s'$ as follows $s \OTarrow {} s_1 \OTarrow {} \ldots \OTarrow {} s_n  \OTarrow {} s'$, we proceed by induction on the length of the inference of  ${s \OTWeakarrow {\alpha} s'}$ (introduced in Definition \ref{def:buildweakOT}).
-First, if  $\overline{\gamma}=\emptyset$ then using rule (1) we can directly conclude  $s=s'$ and $\alpha =\tau$.
-Otherwise, using  rule (2)  we have  s $\OTarrow {\alpha} s'$ and forall $j$, $\gamma_j=\vis{\beta_j}$.
-Second, using rule (3)  we have ${s \OTWeakarrow {\alpha} s'}$ implies ${s \OTWeakarrow {\tau} s_1} \OTWeakarrow {\alpha} s_2  \OTWeakarrow {\tau} s'$ and forall $j$, $\gamma_j = \gamma_{1j}\,\dotcup\,\gamma_{2j}\,\dotcup\,\gamma_{3j}$, and by induction hypothesis this means that there exist $s, s'$  such that $ s \OTarrow {\alpha} s'$ and $j$, $\gamma_{2j}=\vis{\beta_j}$.
-\end{proof}   
-\end{lemma}
-
-\TODO{I am not sure that we have the same states between open auto 
-and weak auto}
-
 \begin{lemma} Let $A = <J,\mathcal{S}, s_0,
@@
 $
-s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s', \quad
-\overline{\gamma}=\biguplus_{i=0}^n \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^m \vis{\overline{\beta^3_i}}
+s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
+\displaystyle{\overline{\gamma}=\mybigdotcup_{i=0}^n \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\overline{\beta^3_i}}}
 \\
@@
 As the condition holds for $l$, it means that there is $n$  $m$, $n'$,$m'$ such that $l=n+m+1$, and $l+1=n'+m'+1$ and either $n'=n+1$ or $m'=m+1$ (exclusively).
-We consider the case $n'=n+1$, $m'=m+1$ is similar. Side conditions are omitted for readability. We first focus on the left part of the disjunction. Suppose we have:
+We consider the case $n'=n+1$, and $m'=m+1$ are similar. Side conditions are omitted for readability. We first focus on the left part of the disjunction. Suppose we have:
 \begin{mathpar}
@@
        \bigvee\\   
- \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\Big)  \implies  {
+ \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)  \implies  {
 \openrule
@@
 \begin{mathpar}
-\Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\Big)
+\Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
 \end{mathpar}
@@
 \begin{mathpar}
-{ \openrule
+{\openrule
          {
@@
 				 } {s \OTWeakarrow {\tau} s} \in \WT
-} \implies \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\Big)
+}\! \implies\! \Big(\alpha = \tau \wedge \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
 \end{mathpar}
@@
 s=s^1_0 \wedge s^1_{n_1}\!=s_1,
-\overline{\gamma_1}=\biguplus_{i=0}^{n_1} \vis{\overline{\beta^1_i}}, 
+\displaystyle{\overline{\gamma_1}=\mybigdotcup_{i=0}^{n_1} \vis{\overline{\beta^1_i}}}, 
 \Pred_1\!=\!\bigwedge_{i=0}^{n_1}\Pred^1_i, \Post_1= \biguplus_{i=0}^{n_1} \Post_i^1\\
@@
 
-\item Similarly, we have: 
+\item Similarly, a series of $m_1=n+m+1$  open transitions can be simplified: 
 \begin{mathpar}
@@
 s_2=s^3_0 \wedge s^1_{m_1}=s',
-\overline{\gamma_3}=\biguplus_{i=0}^{m_1} \vis{\overline{\beta^3_i}},
+\displaystyle{\overline{\gamma_3}=\mybigdotcup_{i=0}^{m_1} \vis{\overline{\beta^3_i}}},
 \Pred_3\!=\!\bigwedge_{i=0}^{m_1}\Pred^3_i,\Post_3\!=\! \biguplus_{i=0}^{m_1} \Post_i^3\\
@@
 s_1=s^1_0 \wedge s^1_n=s^2_0 \wedge s'^2 = s^3_0 \wedge s^3_{m_2}=s_2,
-\overline{\gamma_2}=\biguplus_{i=0}^{n_2} \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^{m_2} \vis{\overline{\beta^3_i}}
+\displaystyle{\overline{\gamma_2}=\mybigdotcup_{i=0}^{n_2} \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}}  \mybigdotcup_{i=0}^{m_2} \vis{\overline{\beta^3_i}}}
 \\
@@
 ~~\\
-
 Therefore, we can deduce that:
@@
 where\\
-$
-s_1\!=\!s^1_0 \wedge s^1_{n_1+n_2}\!=s^2 \wedge s'^2 = s^3_0 \wedge s^3_{m_1+m_2}\!=\!s',
-\overline{\gamma}=\biguplus_{i=0}^{n_1+n_2} \vis{\overline{\beta^1_i}} 
-\dotcup  \vis{\overline{\beta^2}} \dotcup \biguplus_{i=0}^{m_1+m_2} \vis{\overline{\beta^3_i}}
+\[
+\begin{array}{l}
+s_1\!=\!s^1_0 \wedge s^1_{n_1+n_2}\!=s^2 \wedge s'^2 = s^3_0 \wedge s^3_{m_1+m_2}\!=\!s'\\
+\displaystyle{\overline{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2} \vis{\overline{\beta^1_i}}
+\dotcup\vis{\overline{\beta^2}}\dotcup\!\mybigdotcup_{i=0}^{m_1+m_2}\vis{\overline{\beta^3_i}}
+}\\
+\displaystyle{\Pred=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred\,^2\subst{ \biguplus_{i=0}^{n_2}\Post^1_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^1_i}}
 \\
-\Pred=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred\,^2\subst{ \biguplus_{i=0}^{n_2}\Post^1_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^1_i}
-\\
-\Post= ({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\biguplus_{i=0}^{n_2} \Post^1_i}})^{k\in K}
-$
-
+\displaystyle{\Post= ({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\biguplus_{i=0}^{n_2} \Post^1_i}})^{k\in K}}
+\end{array}
+\]
 \end{itemize}
@@
 Using this lemma, it is straightforward to see that....
+
+\begin{corollary} The definition of weak bisimulation given in  Definition \ref{def-Weak-bisim} is equivalent to the following weak FH-bisimulation: Let $A_1 = <J,\mathcal{S}_1, s_0,
+    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata.
+Let $<J,\mathcal{S}_1, s_0,
+    \WT_1>$ and $<J,\mathcal{S}_2,t_0,  \WT_2>$ be the
+weak open automata derived from $A_1$ and $A_2$ respectively.
+For any  states
+$s\in\mathcal{S}_1$ and
+$t\in\mathcal{S}_2$ such that $(s,t|\Pred)\in\mathcal{R}$, we 
+   have:
+
+ \begin{itemize}
+ \item  For any open transition $\symb{WOT}$ in $\WT_1$:
+ \begin{mathpar}
+     \openrule
+         {
+           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
+         {s \OTWeakarrow {\alpha} s'}
+
+\end{mathpar}
+ there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
+ \begin{mathpar}
+    \openrule
+         {
+           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {t \OTWeakarrow {\alpha_x} t_x}
+\end{mathpar}
+ such that  $\forall x, \{j\in J_1|\gamma_j\neq\emptyset\}=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
+ and  \\
+$\Pred \land \Pred_{OT}\\
+\displaystyle{\implies\!\!\! \bigvee_{x\in X}
+   \left( \forall j\in J_x.\gamma_j=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
+     \land \alpha\!=\!\alpha_x \land  
+     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)}$
+
+ \item  and symmetrically any open transition from $\symb{WOT}$ in $\WT_2$ can be 
+      covered by a set of weak transitions from $s$ in $\WT_1$.
+ \end{itemize}
+
+\end{corollary}
+
 \begin{lemma}
@@
        	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
-       	\left( \forall j. \gamma_{jpx}=\gamma_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
+       	\left( \forall j. \vis{\beta_{jpx}}=\gamma_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
        	\land \alpha_{px}\!=\!\alpha_{pxy} \land

### 2018-09-28 2016-Weak-FH-Bisim/WeakBisim.tex

@@
 %\def\Actionalg{\mathcal{A}}
+\TODO{Attention: la notation of term algebra is the same for set of transition.}
 
@@
          {
-           \beta_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
+           \beta_j^{j\in J'},\Pred_{OT},\Post_{OT}}
          {s \OTarrow {\alpha} s'}
@@
 \end{mathpar}
- such that  $\forall x, J_1=J_{x}, \exists \Pred_{s',t_x}. (s',t_x|\Pred_{s',t_x})\in 
+ such that  $\forall x, J'=J_{x}, \exists \Pred_{s',t_x}. (s',t_x|\Pred_{s',t_x})\in 
  \mathcal{R}$; 
@@
 \end{mathpar}
- such that  $\forall x, \{j\in J_1|\beta_j\neq\tau\}=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
+ such that  $\forall x, \{j\in J'|\beta_j\neq\tau\}=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
  and  \\
@@
 
+\TODO{Lemma revu mais convaincant...}
+
 \begin{lemma} Let $A = <J,\mathcal{S}, s_0,
@@
     \WT>$ be the
-weak open automata derived from $A$.  For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:
-
+weak open automata derived from $A$.  \\
+%For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
+There exist  sets of $\beta^1_i$, $\beta^2_i$, and $\beta^3_i$, $\Pred^1_i$, $\Pred^3_i$, $\Post^1_i$, and  $\Pred^2$, $\Post^2$ s.t.:
 \begin{mathpar}
@@
        \bigvee\\   
- \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)  \Longleftrightarrow  {
+ \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
+ \end{mathpar}
+If only if there exist a set of $\beta$, $\Pred$, $\Post$ s.t.
+ \begin{mathpar}
+%   \Longleftrightarrow  {
 \openrule
@@
 				 } {s \OTWeakarrow {\alpha} s'} \in\WT
-}
+%}
 \end{mathpar}
@@
     {
-       \overline{\beta^3_i},\Pred^3_i,\Post^3_i   }
-         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}         \bigg)
+       \overline{\beta^2_i},\Pred^2_i,\Post^2_i   }
+         {s^2_i \OTarrow {\tau} s^2_{i+1}} \in \mathcal{T}         \bigg)
 \end{mathpar}
@@
 $
-s_2=s^3_0 \wedge s^1_{m_1}=s',
-\displaystyle{\overline{\gamma_3}=\mybigdotcup_{i=0}^{m_1} \vis{\overline{\beta^3_i}}},
-\Pred_3\!=\!\bigwedge_{i=0}^{m_1}\Pred^3_i,\Post_3\!=\! \biguplus_{i=0}^{m_1} \Post_i^3\\
+s_2=s^2_0 \wedge s^2_{m_1}=s',
+\displaystyle{\overline{\gamma_2}=\mybigdotcup_{i=0}^{m_1} \vis{\overline{\beta^2_i}}},
+\Pred_3\!=\!\bigwedge_{i=0}^{m_1}\Pred^2_i,\Post_2\!=\! \biguplus_{i=0}^{m_1} \Post_i^2\\
 $
@@
     {
-       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
-         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}  \wedge
+       \overline{\beta^3_i},\Pred^3_i,\Post^3_i   }
+         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}  \wedge
 
@@
          {
-           \overline{\beta^2},\Pred^2,\Post^2 }
-         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
+           \overline{\beta^4},\Pred^4,\Post^4 }
+         {s^4 \OTarrow {\alpha} s'^4} \in \mathcal{T}
  \wedge
@@
          {
-           \overline{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
-         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
+           \overline{\beta^5_i},\Pred^5_i,({x^5_k\gets e^5_k})^{k\in K}    }
+         {s^5_i \OTarrow {\tau} s^5_{i+1}} \in \mathcal{T}
 \Bigg)         
@@
 $
-s_1=s^1_0 \wedge s^1_n=s^2_0 \wedge s'^2 = s^3_0 \wedge s^3_{m_2}=s_2,
-\displaystyle{\overline{\gamma_2}=\mybigdotcup_{i=0}^{n_2} \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}}  \mybigdotcup_{i=0}^{m_2} \vis{\overline{\beta^3_i}}}
+s_1=s^3_0 \wedge s^3_{n_2}=s^4 \wedge s'^4 = s^5_0 \wedge s^5_{m_2}=s_2,
+\displaystyle{\overline{\gamma_2}=\mybigdotcup_{i=0}^{n_2} \vis{\overline{\beta^3_i}} \dotcup  \vis{\overline{\beta^4}}  \mybigdotcup_{i=0}^{m_2} \vis{\overline{\beta^5_i}}}
 \\
-\Pred_2=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred\,^2\subst{ \biguplus_{i=0}^{n_2}\Post^1_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^1_i}
+\Pred_2=\bigwedge_{i=0}^{n_2}\Pred^3_i\land\Pred\,^4\subst{ \biguplus_{i=0}^{n_2}\Post^3_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred\,^5_i\subst{\Post^4}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^1_i}
 \\
-\Post_2= ({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\biguplus_{i=0}^{n_2} \Post^1_i}})^{k\in K}
+\Post_2= ({x^5_k\gets (e^5_k\subst {\Post^4})\subst{\biguplus_{i=0}^{n_2} \Post^3_i}})^{k\in K}
 $
@@
     {
-       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
-         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in\mathcal{T} \wedge
+       \overline{\beta^6_i},\Pred^6_i,\Post^6_i   }
+         {s^6_i \OTarrow {\tau} s^6_{i+1}} \in\mathcal{T} \wedge
 
@@
          {
-           \overline{\beta^2},\Pred^2,\Post^2 }
-         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
+           \overline{\beta^7},\Pred^7,\Post^7 }
+         {s^7 \OTarrow {\alpha} s'^7} \in \mathcal{T}
 \wedge
 \forall i \in [0\ldots(m_1\!+\!m_2)].\openrule
-         {\overline{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
-         {s^3_i\OTarrow {\tau} s^3_{i+1}}\in\mathcal{T}\Bigg)  
+         {\overline{\beta^8_i},\Pred^8_i,({x^8_k\gets e^8_k})^{k\in K}    }
+         {s^8_i\OTarrow {\tau} s^8_{i+1}}\in\mathcal{T}\Bigg)  
 \end{mathpar}
 
-where\\
-\[
-\begin{array}{l}
-s_1\!=\!s^1_0 \wedge s^1_{n_1+n_2}\!=s^2 \wedge s'^2 = s^3_0 \wedge s^3_{m_1+m_2}\!=\!s'\\
-\displaystyle{\overline{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2} \vis{\overline{\beta^1_i}}
-\dotcup\vis{\overline{\beta^2}}\dotcup\!\mybigdotcup_{i=0}^{m_1+m_2}\vis{\overline{\beta^3_i}}
+such that\\
+$
+s_i^6= \left\{
+ \begin{array}{ll}
+s_i^1 & \mbox{if }i<n_1\\
+s_{i-n_1}^3 & \mbox{if }i\geq n_1\\
+\end{array}
+\right. \, \wedge \,
+s_i^8= \left\{
+ \begin{array}{ll}
+s_i^2 & \mbox{if }i<m_1\\
+s_{i-m_1}^5 & \mbox{if }i\geq m_1\\
+\end{array}
+\right. \\
+s\!=\!s^6_0 \wedge s^6_{n_1+n_2}\!=s^7 \wedge s'^7 = s^8_0 \wedge s^8_{m_1+m_2}\!=\!s'\\
+~~\\
+\displaystyle{\overline{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2}\!\! \vis{\overline{\beta^6_i}}
+\dotcup\vis{\overline{\beta^7}}\dotcup\!\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\overline{\beta^8_i}}
 }\\
-\displaystyle{\Pred=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred\,^2\subst{ \biguplus_{i=0}^{n_2}\Post^1_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^1_i}}
+\displaystyle{\Pred=\bigwedge_{i=0}^{n_2}\Pred^6_i\land\Pred^7\subst{ \biguplus_{i=0}^{n_2}\Post^6_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred^6_i\subst{\Post^7}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^6_i}}
 \\
-\displaystyle{\Post= ({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\biguplus_{i=0}^{n_2} \Post^1_i}})^{k\in K}}
-\end{array}
-\]
+\displaystyle{\Post= ({x^8_k\gets (e^8_k\subst {\Post^7})\subst{\biguplus_{i=0}^{n_2} \Post^6_i}})^{k\in K}}
+$
 \end{itemize}

### 2018-10-10 2016-Weak-FH-Bisim/WeakBisim.tex
sketch of proof for discussion

@@
 
-\begin{lemma} Let $A = <J,\mathcal{S}, s_0,
+\begin{lemma}
+\label{lem-rel-OT-WOT} Let $A = <J,\mathcal{S}, s_0,
     \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
@@
 \end{corollary}
-
+\begin{proof}
+Sketch for discussion.\\
+
+1) By lemma \ref{lem-rel-OT-WOT} we have:
+
+\begin{mathpar}
+\openrule
+         {
+           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {t \OTWeakarrow {\alpha_x} t_x}
+         \implies
+
+ \Bigg(\forall i \in [0\ldots n].\openrule
+    {
+       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
+         {s^1_i \OTarrow {\tau} s^1_{i}} \in \mathcal{T} \quad \wedge
+\quad
+\openrule
+         {
+           \overline{\beta^2},\Pred\,^2,\Post^2 }
+         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
+\quad \wedge\\
+\forall i \in [0\ldots m].\openrule
+         {
+           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
+         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
+\Bigg) 
+ \end{mathpar}
+2) From Definition \ref{def-Weak-bisim} we have:
+
+For each open transition $OT$ in $\mathcal{T}_1$:
+ \begin{mathpar}
+     \openrule
+         {
+           \beta_j^{j\in J'},\Pred_{OT},\Post_{OT}}
+         {s \OTarrow {\alpha} s'}
+
+\end{mathpar}
+ there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
+ \begin{mathpar}
+    \openrule
+         {
+           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {t \OTWeakarrow {\alpha_x} t_x}
+\end{mathpar}
+ such that  $\forall x, \{j\in J'|\beta_j\neq\tau\}=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
+ and  \\
+ $\Pred \land \Pred_{OT}\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
+   \left( \forall j\in J_x. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
+     \land \alpha\!=\!\alpha_x \land  
+     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
+
+ 3) From Definition \ref{def:buildweakOT} we have:
+
+ \begin{mathpar}
+  \mprset {vskip=.5ex}
+\inferrule {\openrule
+         {
+           \overline{\gamma_1},\Pred_1,\Post_1   }
+         {s \OTWeakarrow {\tau} s_1} \in \WT
+\qquad
+\openrule
+         {
+           \overline{\gamma_2},\Pred_2,\Post_2  }
+         {s_1 \OTWeakarrow {\alpha} s_2} \in \WT
+\qquad
+\openrule
+         {
+           \overline{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
+         {s_2 \OTWeakarrow {\tau} s'} \in\WT
+\\
+\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
+}
+{
+\openrule
+         {
+           \overline{\gamma_1}\dotcup \overline{\gamma_2}\dotcup\overline{\gamma_3},
+		\Pred,
+				({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K} } 
+         {s \OTWeakarrow {\alpha} s'} \in\WT
+} \WTTrois
+\end{mathpar}
+
+ \TODO{Trouver comment decrire la recurrence/fusionner les Pred}
+
+\end{proof}
+------------------------------------------------------
 \begin{lemma}
@@
 \TODO{Underneath is the rules of the closed semantics. Not sure we
-  should keep them here, but we mentionned we should have a proof of
+  should keep them here, but we mentioned we should have a proof of
   the relation between the 2 semantics... In an extended version I

### 2018-10-11 2016-Weak-FH-Bisim/WeakBisim.tex
small changes : vis is v and overline is set

@@
 %family is denoted $\emptyset$. We
-%denote classically with an overline -- $\overline{a}$  -- a family when the indexing set 
+%denote classically with an overline -- $\set{a}$  -- a family when the indexing set 
 %is
@@
     J}\rangle} s'\in \to \} \\
-\Sortop(\mylangle \overline{\pNet}\!, %\pNet_i^{i\in I}, 
-\overline{\Sort},
-\overline{\symb{SV}}\myrangle)
-=\{\alpha' |\, \SV{\overline{\alpha}}{\alpha'}{e_b}\in\set{\symb{SV}}\}
+\Sortop(\mylangle \set{\pNet}\!, %\pNet_i^{i\in I}, 
+\set{\Sort},
+\set{\symb{SV}}\myrangle)
+=\{\alpha' |\, \SV{\set{\alpha}}{\alpha'}{e_b}\in\set{\symb{SV}}\}
 \end{array}
@@
 \Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset\\
-\Holes(\mylangle \pNet_i^{i\in I}\!,\overline{\Sort}, \overline{\symb{SV}}\myrangle) 
+\Holes(\mylangle \pNet_i^{i\in I}\!,\set{\Sort}, \set{\symb{SV}}\myrangle) 
 =J\uplus{\displaystyle \bigcup_{i\in 
@@
 \Leaves(\mylangle \pNet_i^{i\in I}\!,%Sort_j^{j\in J}
-\overline{\Sort}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \biguplus_{i\in 
+\set{\Sort}\!, \set{\symb{SV}}\myrangle) = {\displaystyle \biguplus_{i\in 
 I}\Leaves(\pNet_i)\uplus\{i\mapsto \pNet_i|\pNet_i \text{ is a }\pLTS\}}
@@
 	An open pNet: $\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
-	\overline{\symb{SV}}\myrangle$
+	\set{\symb{SV}}\myrangle$
  can be (partially) filled by providing  a pNet $\pNetQ$ of the
@@
 	\pNet_i^{i\in I}\uplus\{j_0\mapsto \pNetQ\},\Sort_j^{j\in J\setminus \{j_0\}},
-	\overline{\symb{SV}}\myrangle
+	\set{\symb{SV}}\myrangle
 	\]
@@
  \begin{mathpar}
-%    \left( fresh \ \overline{\alpha_i}, \overline{b_j}, v_x.\ \
+%    \left( fresh \ \set{\alpha_i}, \set{b_j}, v_x.\ \
     \openrule
@@
 %Let
-%$\mylangle\overline{\pNet},\overline{\Sort},\overline{\symb{SV}}\myrangle$
+%$\mylangle\set{\pNet},\set{\Sort},\set{\symb{SV}}\myrangle$
 %be a pNet. 
@@
 %		\item $J$ is the set of holes: $Holes(p)= J$. 
-		%  \item $\overline{L}^L = Leaves(p), \overline{H}^J = Holes(p)$
+		%  \item $\set{L}^L = Leaves(p), \set{H}^J = Holes(p)$
 %		\item ${\mathcal{S}} = States(p)$ and $s_0 = InitState(p)$
@@
     {
-\Leaves(\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in 
+\Leaves(\mylangle \set{\pNet}, \set{\Sort}, \symb{SV}_k^{k\in 
     	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
@@
     }
-    {\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
+    {\mylangle \set{\pNet}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
     	\models
@@
 	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
-	\overline{\symb{SV}}\myrangle$.
+	\set{\symb{SV}}\myrangle$.
 	Let $j_0\in J$ be a hole. Let $\pNetQ$ and $\pNetQ'$ be two FH-bisimilar pNets such that 
@@
 	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
-	\overline{\symb{SV}}\myrangle$ and 	$\pNet' = \mylangle {\pNet'}_i^{i\in I}, 
+	\set{\symb{SV}}\myrangle$ and 	$\pNet' = \mylangle {\pNet'}_i^{i\in I}, 
 	\Sort_j^{j\in 
-	J}, 	\overline{\symb{SV'}}\myrangle$ 
+	J}, 	\set{\symb{SV'}}\myrangle$ 
 	(recall they must have the same holes to be bisimilar).
@@
 Intuition: tau is non observable if the automaton allows any tau transition from holes, and the global transition resulting from a tau in a hole is a tau transition not changing the action state.
-\TODO{Id(s) is the identity function on variables of state s}
+We define $\Id(s)$ as the identity function on variables of state s.
 \begin{definition}[Non-observability of silent actions]
@@
 \]
+\TODO{question : it looks like we can have 2 holes doing a tau and observe this ; I belive this is not safe (LUDO)}
 \end{enumerate}
 \end{definition}
+The first statement of the definition state that the open automaton must allow a hole to do a silent action at any time, and must not observe it, i.e.
+cannot change its internal state because a hole did a $\tau$ transition.
+The second statement ensures that there cannot be in the open automaton other transitions that would be able to observe a silent action from a hole.
 
@@
 
-We define $\vis{\overline\beta}$ as the mapping $\overline\beta$  without  invisible actions but where each element is now a list (if length 1).\\ $\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}$ s.t.
+We define $\vis{\set\beta}$ as the mapping $\set\beta$  without  invisible actions but where each element is now a list (if length 1).\\ $\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}$ s.t.
 $I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}$.
@@
          {
-           \overline{\beta},\Pred,\Post}
+           \set{\beta},\Pred,\Post}
          {s \OTarrow {\alpha} s'} \in \mathcal{T}
@@
          {
-           \vis{\overline{\beta}}\!,\Pred,\Post
+           \vis{\set{\beta}}\!,\Pred,\Post
 				 } {s \OTWeakarrow {\alpha} s'} \in \WT
@@
 %         {
-%           \overline{\beta},\Pred,\Post}
+%           \set{\beta},\Pred,\Post}
 %         {s \OTarrow {\tau} s'} \in \mathcal{T}
@@
 %         {
-%           \overline{\gamma},\Pred\,',({x_k\gets e_k})^{k\in K}   }
+%           \set{\gamma},\Pred\,',({x_k\gets e_k})^{k\in K}   }
 %         {s' \OTWeakarrow {\tau} s''} \in \WT
@@
 %         {
-%           \vis{\overline{\beta}}\dotcup\overline{\gamma},\Pred\land\Pred\,'\subst{\Post\,},
+%           \vis{\set{\beta}}\dotcup\set{\gamma},\Pred\land\Pred\,'\subst{\Post\,},
 %				({x_k\gets (e_k\subst{\Post\,})})^{k\in K} } 
@@
          {
-           \overline{\gamma_1},\Pred_1,\Post_1   }
+           \set{\gamma_1},\Pred_1,\Post_1   }
          {s \OTWeakarrow {\tau} s_1} \in \WT
@@
          {
-           \overline{\gamma_2},\Pred_2,\Post_2  }
+           \set{\gamma_2},\Pred_2,\Post_2  }
          {s_1 \OTWeakarrow {\alpha} s_2} \in \WT
@@
          {
-           \overline{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
+           \set{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
          {s_2 \OTWeakarrow {\tau} s'} \in\WT
@@
          {
-           \overline{\gamma_1}\dotcup \overline{\gamma_2}\dotcup\overline{\gamma_3},
+           \set{\gamma_1}\dotcup \set{\gamma_2}\dotcup\set{\gamma_3},
 		\Pred,
@@
 %%          {
-%%            \overline{\gamma_1},\Pred_1,\Post_1   }
+%%            \set{\gamma_1},\Pred_1,\Post_1   }
 %%          {s \OTWeakarrow {\tau} s_1}
@@
 %%          {
-%%            \overline{\gamma_2},\Pred_2,\Post_2   }
+%%            \set{\gamma_2},\Pred_2,\Post_2   }
 %%          {s_1 \OTWeakarrow {\alpha} s_2}
@@
 %%          {
-%%            \overline{\gamma_3},\Pred_3,\Post_3   }
+%%            \set{\gamma_3},\Pred_3,\Post_3   }
 %%          {s_2 \OTWeakarrow {\tau} s_3}
@@
 %%          {
-%%            \overline{\gamma},\Pred,\Post   }
+%%            \set{\gamma},\Pred,\Post   }
 %%          {s \OTWeakarrow {\alpha} s_3}
@@
 \begin{definition}[Non-observability of silent actions for pNets]~\\
-A pNet $\mylangle \pNet_i^{i\in I} , \Sort_j^{j\in J}, \overline{\symb{SV}}\myrangle$
- \emph{cannot observe silent actions} if it verifies:\\ $\forall i\in I\uplus J.\, \SV{(i\mapsto \tau)}{\tau}{\True}\in \overline{\symb{SV}}$ and $\forall SV_k\in \overline{\symb{SV}}, \forall i,j\in I_k\uplus J_k.\,i\neq j \Rightarrow \alpha'_k\neq\tau$
+A pNet $\mylangle \pNet_i^{i\in I} , \Sort_j^{j\in J}, \set{\symb{SV}}\myrangle$
+ \emph{cannot observe silent actions} if it verifies:\\ $\forall i\in I\uplus J.\, \SV{(i\mapsto \tau)}{\tau}{\True}\in \set{\symb{SV}}$ and $\forall SV_k\in \set{\symb{SV}}, \forall i,j\in I_k\uplus J_k.\,i\neq j \Rightarrow \alpha'_k\neq\tau$
 \end{definition}
@@
 	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
-	\overline{\symb{SV}}\myrangle$.
+	\set{\symb{SV}}\myrangle$.
 	Let $j_0\in J$ be a hole. Let $\pNetQ$ and $Q'$ be two weak FH-bisimilar pNets such that 
@@
 	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
-	\overline{\symb{SV}}\myrangle$ and 	$\pNet' = \mylangle {\pNet'}_i^{i\in I}, 
+	\set{\symb{SV}}\myrangle$ and 	$\pNet' = \mylangle {\pNet'}_i^{i\in I}, 
 	\Sort_j^{j\in 
-	J}, 	\overline{\symb{SV'}}\myrangle$ that are weak FH-bisimilar
+	J}, 	\set{\symb{SV'}}\myrangle$ that are weak FH-bisimilar
 	(recall they must have the same holes to be bisimilar).
@@
 %
-%%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
+%%    \left( fresh \ \set{a_i}, \set{b_j}, v_x.\ \
 %\inferrule*[myfraction=\reddottedrule]
@@
        	\begin{mathpar} 
-       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
+       	%    \left( fresh \ \set{a_i}, \set{b_j}, v_x.\ \
        	\openrule
@@
        	\begin{mathpar}  	
-       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
+       	%    \left( fresh \ \set{a_i}, \set{b_j}, v_x.\ \
        	\openrule
@@
 			\begin{mathpar}
-			%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
+			%    \left( fresh \ \set{a_i}, \set{b_j}, v_x.\ \
 			P'\models\openrule
@@
     {
-       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
+       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
          {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
@@
          {
-           \overline{\beta^2},\Pred\,^2,\Post^2 }
+           \set{\beta^2},\Pred\,^2,\Post^2 }
          {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
@@
          {
-           \overline{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
+           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
          {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
@@
        \bigvee\\   
- \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
+ \Big(\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
  \end{mathpar}
-If only if there exist a set of $\beta$, $\Pred$, $\Post$ s.t.
+If only if there exist $\set{\gamma}$, $\Pred$, $\Post$ s.t.
  \begin{mathpar}
@@
          {
-           \overline{\gamma},
+           \set{\gamma},
 		\Pred, \Post
@@
 s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
-\displaystyle{\overline{\gamma}=\mybigdotcup_{i=0}^n \vis{\overline{\beta^1_i}} \dotcup  \vis{\overline{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\overline{\beta^3_i}}}
+\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i}}}
 \\
@@
 %         {
-%           \overline{\beta},\Pred,\Post}
+%           \set{\beta},\Pred,\Post}
 %         {s \OTarrow {\alpha} s'} \in \mathcal{T}
@@
          {
-           \overline{\beta},\Pred,\Post}
+           \set{\beta},\Pred,\Post}
          {s \OTarrow {\alpha} s'} \in \mathcal{T} \implies 
@@
        \bigvee\\   
- \Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)  \implies  {
-\openrule
-         {
-           \overline{\gamma},
+ \Big(\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)  \implies  {
+\openrule
+         {
+           \set{\gamma},
 		\Pred, \Post
@@
          {
-           \overline{\beta},\Pred,\Post}
+           \set{\beta},\Pred,\Post}
          {s \OTarrow {\tau} s'} \in \mathcal{T}
@@
          {
-           \vis{\overline{\beta}}\!,\Pred,\Post
+           \vis{\set{\beta}}\!,\Pred,\Post
 				 } {s \OTWeakarrow {\tau} s'} \in \WT
@@
          {
-           \vis{\overline{\beta}},\Pred,\Post   }
+           \vis{\set{\beta}},\Pred,\Post   }
          {s \OTWeakarrow {\tau} s'} \in \WT
@@
          {
-          \vis{\overline{\beta}} \dotcup \overline{\gamma},
+          \vis{\set{\beta}} \dotcup \set{\gamma},
 		\Pred,
@@
 \begin{mathpar}
-\Big(\alpha = \tau \wedge  \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
+\Big(\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
 \end{mathpar}
@@
 				 } {s \OTWeakarrow {\tau} s} \in \WT
-}\! \implies\! \Big(\alpha = \tau \wedge \overline{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
+}\! \implies\! \Big(\alpha = \tau \wedge \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
 \end{mathpar}
@@
          {
-           \overline{\gamma},\Pred,\Post}
+           \set{\gamma},\Pred,\Post}
          {s \OTWeakarrow {\alpha} s'} \in \WT \implies
@@
          {
-           \overline{\beta},\Pred,\Post}
+           \set{\beta},\Pred,\Post}
          {s \OTWeakarrow {\alpha} s'} \in \mathcal{T}         
 \end{mathpar}
-where $\overline{\gamma} = \vis{\overline{\beta}}$.
+where $\set{\gamma} = \vis{\set{\beta}}$.
 These two cases prove the implication with $n=0$ and $m=0$.
@@
 %where 
-%$\overline{\gamma}=\overline{\gamma_1} \dotcup \overline{\gamma_2} \dotcup \overline{\gamma_3}$,
+%$\set{\gamma}=\set{\gamma_1} \dotcup \set{\gamma_2} \dotcup \set{\gamma_3}$,
 %$\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}$, and $\Post= ({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K}$
@@
          {
-           \overline{\gamma_1},\Pred_1,\Post_1   }
+           \set{\gamma_1},\Pred_1,\Post_1   }
          {s \OTWeakarrow {\tau} s_1} \in\! \WT \bigg)
@@
     {
-       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
+       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
          {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}         \bigg)
@@
 s=s^1_0 \wedge s^1_{n_1}\!=s_1,
-\displaystyle{\overline{\gamma_1}=\mybigdotcup_{i=0}^{n_1} \vis{\overline{\beta^1_i}}}, 
+\displaystyle{\set{\gamma_1}=\mybigdotcup_{i=0}^{n_1} \vis{\set{\beta^1_i}}}, 
 \Pred_1\!=\!\bigwedge_{i=0}^{n_1}\Pred^1_i, \Post_1= \biguplus_{i=0}^{n_1} \Post_i^1\\
@@
          {
-           \overline{\gamma_3},\Pred_3,\Post_3   }
+           \set{\gamma_3},\Pred_3,\Post_3   }
          {s_2 \OTWeakarrow {\tau} s'} \in\! \WT
@@
     {
-       \overline{\beta^2_i},\Pred^2_i,\Post^2_i   }
+       \set{\beta^2_i},\Pred^2_i,\Post^2_i   }
          {s^2_i \OTarrow {\tau} s^2_{i+1}} \in \mathcal{T}         \bigg)
@@
 s_2=s^2_0 \wedge s^2_{m_1}=s',
-\displaystyle{\overline{\gamma_2}=\mybigdotcup_{i=0}^{m_1} \vis{\overline{\beta^2_i}}},
+\displaystyle{\set{\gamma_2}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^2_i}}},
 \Pred_3\!=\!\bigwedge_{i=0}^{m_1}\Pred^2_i,\Post_2\!=\! \biguplus_{i=0}^{m_1} \Post_i^2\\
@@
          {
-           \overline{\gamma_2},\Pred_2,\Post_2  }
+           \set{\gamma_2},\Pred_2,\Post_2  }
          {s_1 \OTWeakarrow {\alpha} s_2} \in\! \WT\bigg)
@@
     {
-       \overline{\beta^3_i},\Pred^3_i,\Post^3_i   }
+       \set{\beta^3_i},\Pred^3_i,\Post^3_i   }
          {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}  \wedge
@@
          {
-           \overline{\beta^4},\Pred^4,\Post^4 }
+           \set{\beta^4},\Pred^4,\Post^4 }
          {s^4 \OTarrow {\alpha} s'^4} \in \mathcal{T}
@@
          {
-           \overline{\beta^5_i},\Pred^5_i,({x^5_k\gets e^5_k})^{k\in K}    }
+           \set{\beta^5_i},\Pred^5_i,({x^5_k\gets e^5_k})^{k\in K}    }
          {s^5_i \OTarrow {\tau} s^5_{i+1}} \in \mathcal{T}
@@
 s_1=s^3_0 \wedge s^3_{n_2}=s^4 \wedge s'^4 = s^5_0 \wedge s^5_{m_2}=s_2,
-\displaystyle{\overline{\gamma_2}=\mybigdotcup_{i=0}^{n_2} \vis{\overline{\beta^3_i}} \dotcup  \vis{\overline{\beta^4}}  \mybigdotcup_{i=0}^{m_2} \vis{\overline{\beta^5_i}}}
+\displaystyle{\set{\gamma_2}=\mybigdotcup_{i=0}^{n_2} \vis{\set{\beta^3_i}} \dotcup  \vis{\set{\beta^4}}  \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^5_i}}}
 \\
@@
          {
-           \overline{\gamma}\!,\Pred,\Post
+           \set{\gamma}\!,\Pred,\Post
 				 } {s \OTWeakarrow {\alpha} s'} \in \WT
@@
     {
-       \overline{\beta^6_i},\Pred^6_i,\Post^6_i   }
+       \set{\beta^6_i},\Pred^6_i,\Post^6_i   }
          {s^6_i \OTarrow {\tau} s^6_{i+1}} \in\mathcal{T} \wedge
@@
          {
-           \overline{\beta^7},\Pred^7,\Post^7 }
+           \set{\beta^7},\Pred^7,\Post^7 }
          {s^7 \OTarrow {\alpha} s'^7} \in \mathcal{T}
@@
 \forall i \in [0\ldots(m_1\!+\!m_2)].\openrule
-         {\overline{\beta^8_i},\Pred^8_i,({x^8_k\gets e^8_k})^{k\in K}    }
+         {\set{\beta^8_i},\Pred^8_i,({x^8_k\gets e^8_k})^{k\in K}    }
          {s^8_i\OTarrow {\tau} s^8_{i+1}}\in\mathcal{T}\Bigg)  
@@
 ~~\\
-\displaystyle{\overline{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2}\!\! \vis{\overline{\beta^6_i}}
-\dotcup\vis{\overline{\beta^7}}\dotcup\!\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\overline{\beta^8_i}}
+\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2}\!\! \vis{\set{\beta^6_i}}
+\dotcup\vis{\set{\beta^7}}\dotcup\!\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta^8_i}}
 }\\
@@
     {
-       \overline{\beta^1_i},\Pred^1_i,\Post^1_i   }
+       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
          {s^1_i \OTarrow {\tau} s^1_{i}} \in \mathcal{T} \quad \wedge
@@
 
-    \inferrule {\phi,\phi'\in\Phi\\ \alpha_l^{l\in L} \to \alpha \in \overline{\symb{SV}}\\\forall i\in I\phi\setminus
+    \inferrule {\phi,\phi'\in\Phi\\ \alpha_l^{l\in L} \to \alpha \in \set{\symb{SV}}\\\forall i\in I\phi\setminus
       L\phi.\,s'_i=s_i
@@
 {\triangleleft s_i^{i\in I\phi}\triangleright \xrightarrow{\alpha\phi'} \triangleleft{s'_i}^{i\in
-        I\phi'}\triangleright  \in \llbracket\mylangle \pNet_i^{i\in I},\emptyset,\overline{\symb{SV}}\myrangle\rrbracket_\Phi}~~{\bf Tr2}
+        I\phi'}\triangleright  \in \llbracket\mylangle \pNet_i^{i\in I},\emptyset,\set{\symb{SV}}\myrangle\rrbracket_\Phi}~~{\bf Tr2}
 \end{mathpar}

### 2018-10-11 2016-Weak-FH-Bisim/WeakBisim.tex
conclusion proof induction

@@
 As the condition holds for $l$, it means that there is $n$  $m$, $n'$,$m'$ such that $l=n+m+1$, and $l+1=n'+m'+1$ and either $n'=n+1$ or $m'=m+1$ (exclusively).
+\LUDO{je trouve toujours ca pas tres correct le coup $l=n+m+1$ donc $l'=(n+1)+m+1$ ou $l'=n+(m+1)+1$ mais bon comme on dirait que ma proposition plait pas, on verra a la review}
 We consider the case $n'=n+1$, and $m'=m+1$ are similar. Side conditions are omitted for readability. We first focus on the left part of the disjunction. Suppose we have:
@@
 
-\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau transitions such $n_1=n+m+1$, hence by simplification we have: 
+\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau transitions such $n_1=n+m+1$, hence by simplification we have (strictly speaking, by induction we might also have the case $\alpha=\tau\land\set \gamma=\emptyset\land \ldots$ but in this case, \WTUn\ allows us to obtain a similar redution with $n_1=1$):
 \begin{mathpar}
@@
 
-\item On the other hand, by induction hypothesis we have:
+\item Concerning the middle reduction, by induction hypothesis there exist a set of transitions in $\mathcal{T}$ such that:
 \begin{mathpar}
@@
 $
+This concludes the inductive step, showing  that the decomposition expressed by the $\Leftarrow$ direction of the lemma is always possible. 
 \end{itemize}
-
 \end{proof}
@@
 
-\begin{corollary} The definition of weak bisimulation given in  Definition \ref{def-Weak-bisim} is equivalent to the following weak FH-bisimulation: Let $A_1 = <J,\mathcal{S}_1, s_0,
+\begin{corollary} The definition of weak bisimulation given in  Definition \ref{def-Weak-bisim} is equivalent to the following one:
+
+ Let $A_1 = <J,\mathcal{S}_1, s_0,
     \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata.

### 2018-10-11 2018-Arch-pNets/arch-pNets.tex
Arch-pNets paper: updated the architecture figure; minor edits

@@
 
-\newcommand{\ordbool}{\ensuremath{\sB^{<}}}
+%% \newcommand{\order}{\leqslant}
+\newcommand{\order}{<}
+\newcommand{\ordbool}{\ensuremath{\sB^{\order}}}
 \newcommand{\data}{\ensuremath{\sD}}
@@
 \newcommand{\actions}[1]{\ensuremath{\cA_{#1}}}
+\newcommand{\exprs}[1]{\ensuremath{\sE_{#1}}}
+\newcommand{\monexprs}[1]{\ensuremath{\sE^{\order}_{#1}}}
+\newcommand{\boolexprs}[1]{\ensuremath{\sB_{#1}}}
 \newcommand{\guards}[1]{\ensuremath{\ordbool_{#1}}}
-\newcommand{\exprs}[1]{\ensuremath{\sE_{#1}}}
-\newcommand{\boolexprs}[1]{\ensuremath{\sB_{#1}}}
 \newcommand{\assigns}[1]{\ensuremath{\sA_{#1}}}
+\newcommand{\updates}[1]{\ensuremath{\sA^{\order}_{#1}}}
 \newcommand{\valuations}[1]{\ensuremath{\data^{#1}}}
 \newcommand{\val}[3][]{\ensuremath{#1{\sigma}^{#2}_{#3}}}
+\newcommand{\emptyassign}{\noop}
 
@@
 \newcommand{\primeit}[1]{#1'}
-\newcommand{\doubleprimeit}[1]{#1''}
+\newcommand{\secondit}[1]{#1''}
 
@@
 \newcommand{\expmix}{\wedge}
-\newcommand{\order}{\leqslant}
 
@@
     \\
+    \monexprs{\#1} &       
+    {\ttfamily\textbackslash monexprs\{\#1\}} &
+    {\ttfamily\textbackslash sE\^{}\{<\}\_\{\#1\}}
+    \\
     \boolexprs{\#1} &       
@@
     {\ttfamily\textbackslash sA\_\{\#1\}}
+    \\
+    \updates{\#1} &
+    {\ttfamily\textbackslash updates\{\#1\}} &
+    {\ttfamily\textbackslash sA\^{}\{<\}\_\{\#1\}}
     \\
@@
     {\ttfamily\textbackslash val[\textbackslash tilde]\{\#2\}\{\#3\}} &
-    {\ttfamily\#1\{\textbackslash sigma\}\^{}\{\#2\}\_\{\#3\}}
+    (optional argument usage examples)
+    \\[6pt]
+    \val[\primeit]{\#2}{\#3} &
+    {\ttfamily\textbackslash val[\textbackslash primeit]\{\#2\}\{\#3\}} &
+    \\[6pt]
+    \val[\secondit]{\#2}{\#3} &
+    {\ttfamily\textbackslash val[\textbackslash secondit]\{\#2\}\{\#3\}} &
   \end{tabular}
@@
 \emph{data expressions} $\exprs{\variables}$ \replaceSB{, including}{and} a set of \emph{Boolean
-expressions} \todoLH{$\mathcal{B} \to g$}\todoSB{change to $\boolexprs{\variables}$?}
-$\guards{\variables}$ ($\guards{\variables}\subseteq\exprs{\variables}$).
+expressions} \todoLH{$\mathcal{B} \to g$}
+$\boolexprs{\variables}\subseteq\exprs{\variables}$.
 On top of $\exprs{\variables}$ we build the \emph{action algebra}
@@
 \]
-to denote the set of \emph{variable assignments}.}
+to denote the set of \emph{variable assignments}.}  We use the symbol
+$\emptyassign$ to denote the empty assignment, \ie an assignment with
+$I = \emptyset$.
 
@@
 
-\addSB{%
-%
 Finally, we assume the existence of a universal data domain
@@
 values of the variable $x$ and the expression $e$ under the
-  valuation $\val{}{}$.  For a valuation $\val{}{} \in
+valuation $\val{}{}$.
+%
+\addSB{
+%
+It is important to observe that in practice, and in the examples of
+this paper, all the variables are sorted, meaning that their values
+can only range over given subsets of $\data$, such as $\sB$ or
+$\sB^<$.  Hence, applied to expressions, valuations should be
+interpreted as partial functions $\exprs{V} \rightharpoonup
+\data$\footnote{
+%
+
+%
+}
+%
+}
+
+For a valuation $\val{}{} \in
 \valuations{V}$ and an assignment $(x_i := e_i)^{i \in I} \in
@@
 %
-}
+Similarly, an assignment $(x_i := e_i)^{i \in I} \in \assigns{V}$ is
+called monotonic if all expressions $e_i^{i \in I}$ are monotonic.
+We will denote $\guards{V} \subset \boolexprs{V}$, $\monexprs{V}
+\subset \exprs{V}$ and $\updates{V} \subset \assigns{V}$ the sets of
+monotonic Boolean and generic expressions and assignments,
+respectively.
+%
 
@@
   \item $P$ is a set of \emph{ports}, with
-    \noteSB{Added this}\hl{$\export : P \rightarrow 2^V$ 
-    the \emph{set of variables exported by each port},}
+    $\export : P \rightarrow 2^V$ 
+    the \emph{set of variables exported by each port},
   \item $\goesto{}\, \subseteq
-    Q \times 2^P \times \guards{V} \times \exprs{V} \times Q$
+    Q \times 2^P \times \guards{V} \times \updates{V} \times Q$
 %
@@
     $\emptyset \neq a \subseteq P$, a monotonic Boolean \emph{guard} $g \in
-    \guards{V}$ and a monotonic \emph{update expression} \todoSB{$e \rightarrow u$}\hl{$e \in
-    \exprs{V}$}.
+    \guards{V}$ and a monotonic \emph{update assignment} \hl{$u \in
+    \updates{V}$}.
   \end{itemize}
@@
 %
-  In practice, component variables are split in two sub-sets:
-  local and exported variables.  Only exported variables belong
-  to the component interface and can be used for the interactions
-  with other components (see \defn{im}).  However, in the context
-  of this paper we can simplify by omitting this separation.
-%
-  }
-%
-  Notations $q \goesto{a, g, e} q'$ and $q \goesto{a, g, e}$ are as usual;
+  In practice, only exported variables, \ie those in the set
+  $\bigcup_{p \in P}\export(p)$, belong to the component interface and
+  can be used for the interactions with other components (see
+  \defn{im}).  However, in the context of this paper we can simplify
+  by omitting this separation.
+%
+  }
+%
+  Notations $q \goesto{a, g, u} q'$ and $q \goesto{a, g, u}$ are as usual;
   for a component $B$, we denote $Q_B$, $q^0_B$, $V_B$, $\val{0}{B}$, $P_B$,
@@
   \centering
-  \includegraphics[width=\columnwidth]{BIPspec-ArchFailureTimerMax-v3}
+  \includegraphics[width=\columnwidth]{BIPspec-ArchFailureTimerMax-v4}
   \caption{The BIP specification of the Failure Monitor architecture}
@@
 \emph{behaviour}.  Transitions are labelled with the ports of the
-corresponding components, Boolean guards and update functions on local
-variables.  For instance the loop transition $\tstate{1}
+corresponding components, Boolean guards and update assignments on local
+variables.  For instance, the loop transition $\tstate{1}
 \goesto{\PortTick, \GuardTick[], \TimerUpd[]} \tstate{1}$ in the
@@
 than $z.u$, where $z = [l, u]$ is a local variable representing an
-interval.  Upon firing, this transition decrements the value of $t$ by
-$1$.  The guard and update function of the transition $\tstate{1}
+interval.  Upon firing, this transition increments the value of $t$ by
+$1$.  The guard and update assignment of the transition $\tstate{1}
 \goesto{\PortResume} \tstate{0}$ are omitted.  The default values are
-the constant predicate $\true$ and the $\mathit{skip}$ operator
-respectively.  The initial valuations $\val{0}{\NameTimer} = \{z
-\mapsto [0,0], t \mapsto 0\}$ and $\val{0}{\NameCtrl} =
+the constant predicate $\true$ and the empty assignment {\emptyassign}
+%$\mathit{skip}$ operator
+respectively.  The initial states \tstate{0} and \cstate{0}, and valuations $\val{0}{\NameTimer} = \{z
+\mapsto \topinterval, t \mapsto 0\}$ and $\val{0}{\NameCtrl} =
 \{\mathit{zone} \mapsto [\mathrm{Min}, \mathrm{Max}]\}$ are shown by
-initialising transitions $\goesto{\TimerInitZone[]} \tstate{0}$ and
-$\goesto{\IntervalInit[]} \cstate{0}$ respectively.  The constants
+incoming arrows $\goesto{\TimerInit[]} \tstate{0}$ and
+$\goesto{\IntervalInit[]} \cstate{0}$, respectively.  The constants
 $\mathrm{Min}$ and $\mathrm{Max}$ are the parameters of the
@@
     \infer{
-      q \goesto{a, g, e} q'
+      q \goesto{a, g, u} q'
       \and
@@
       \and
-      \val[\primeit]{}{} = \tilde{\val{}{}}[e]
+      \val[\primeit]{}{} = \tilde{\val{}{}}[u]
       \and
@@
 
-  An \emph{interaction model over \hl{$(V, P, \export)$}} is a set $\Gamma
-  \subseteq 2^P \times \guards{V} \times \exprs{V}$, such that,
-  for any interaction $(a, g, e) \in \Gamma$, we have
-  $g \in \guards{\export(a)}$ and $e \in \exprs{\export(a)}$.\footnote{%
+  An \emph{interaction model over $(V, P, \export)$} is a set $\Gamma
+  \subseteq 2^P \times \guards{V} \times \updates{V}$, such that,
+  for any interaction $(a, g, u) \in \Gamma$, we have
+  $g \in \guards{\export(a)}$ and $e \in \updates{\export(a)}$.\footnote{%
 %
@@
 %% \noteLH{supp should go outside the definition}
-When speaking of a set of components or interfaces , we will always
+When speaking of a set of components or interfaces, we will always
 assume that it satisfies the disjointness assumption of \defn{im}.
@@
 P_B$).  The precise meaning of this notation will always be clear from
-the context.  Intuitively, for an interaction $(a, g, e)$, $\supp{a}$
+the context.  Intuitively, for an interaction $(a, g, u)$, $\supp{a}$
 denotes the set of the participating components.
@@
     \infer{    
-      (a, g, e) \in \Gamma
+      (a, g, u) \in \Gamma
       \and
@@
       \and
-      \forall i \in \supp{a}, q_i \goesto{a \cap P_i, g_i, e_i} q_i'
+      \forall i \in \supp{a}, q_i \goesto{a \cap P_i, g_i, u_i} q_i'
       \and
@@
       \and
-      e' = e; e_i^{i \in \supp{a}}
+      u' = u; u_i^{i \in \supp{a}}
     }{
-      (q_i)^{i \in I} \goesto{a, g', e'} (q_i')^{i \in I}
+      (q_i)^{i \in I} \goesto{a, g', u'} (q_i')^{i \in I}
     }\,.
@@
 $\NameTimer.\PortStart$ and $\NameCtrl.\PortFail$ are always
-synchronised, since they belong to the same binary sub-connector,
+synchronised, since they belong to exactly one binary sub-connector,
 where they are both synchrons.  In particular, this means that
@@
   } is a strict partial order on interactions: $\pi
-  \subseteq \bigl(2^P \times \guards{V} \times \exprs{V} \bigr)^2$.
+  \subseteq \bigl(2^P \times \guards{V} \times \updates{V} \bigr)^2$.
 
@@
   denote $\filter{\alpha} \bydef{=} \setdefb{\beta \in (2^P \times
-    \guards{V} \times \exprs{V})}{\alpha \prec_\pi \beta}$ the set of
+    \guards{V} \times \updates{V})}{\alpha \prec_\pi \beta}$ the set of
   interactions that have higher priority than $\alpha$.
@@
     \infer{
-      q \goesto{a, g, e} q'
+      \alpha = (a, g, u)
+      \and
+      q \goesto{a, g, u} q'
       \and
       \textstyle
-      g' = g \land \bigwedge_{(b, h, f) \in \filter[q]{\alpha}} \lnot h
+      g' = g \land \bigwedge_{(b, h, w) \in \filter[q]{\alpha}} \lnot h
     }{
-      q \goesto[\pi]{a, g', e} q'
+      q \goesto[\pi]{a, g', u} q'
     }\,, 
@@
 %
-  where $\filter[q]{\alpha} \bydef{=} \filter{\alpha} \cap
-  \setdefb{\beta \in (2^P \times \guards{V} \times \exprs{V})}{q
-    \goesto{\beta}}$.
+  where $\filter[q]{\alpha} \bydef{=} %% \filter{\alpha} \cap
+  %% \setdefb{\beta \in (2^P \times \guards{V} \times \updates{V})}
+  \setdef{\beta \in \filter{\alpha}}{q \goesto{\beta}}$.
   \todoSBin{Add the intuitive explanation}
@@
 In this paper, we will only consider the so-called \emph{maximal
-  progress} priority $\mu$, where $(a, g, e) \prec_\mu (b, h, f)$ iff $a
+  progress} priority $\mu$, where $(a, g, u) \prec_\mu (b, h, w)$ iff $a
 \varsubsetneq b$ (\ie $a \subseteq b$ and $a \neq b$).  In
@@
 %% $a \subset b$ (as sets of ports), $b$ has higher priority than $a$.
-Going back to our running example in \fig{schema:ArchFailure:BIP}, the
+Going back to our running example in \fig{schema:ArchFailure:BIP}, under the maximal progress priority, the
 port $\NameOprnd.\PortFail$ will never fire alone in a global state,
@@
 %
-  \begin{equation}
+  \noteSB{It does, indeed.  To be completely rigorous, I could replace
+    this with something like $\Gamma\uparrow_{P_A}^P$ but this is
+    quite heavy and the dependency is already implicit from the fact
+    that $\Gamma$ is defined on $P_A$}
+%
+  \noteSB{Which one of \eq{im:extension} and \eq{im:extension1} is
+    more intuitive?}
+%
+  \begin{align}
     \label{eq:im:extension}
-    \IMextend{\Gamma}{P} \bydef{=}
+    \IMextend{\Gamma}{P} &\bydef{=}
     \setdefb{
@@
     }
-    ;
-  \end{equation}
-%
-  $\mu$ is the maximal progress priority model.
+    \\
+    \label{eq:im:extension1}
+    &= 
+    \setdefb{
+      (a, g, e)
+    }{
+      a \subseteq P,
+      (a \cap P_A, g, e) \in \Gamma
+    }
+  \end{align}
+%
+  and $\mu$ is the maximal progress priority model.
 \end{definition}
@@
   $\val[\doubletilde]{}{1}[e^1; (e_1, e_b)] =
-  (\val[\primeit]{}{1}, \val[\doubleprimeit]{}{})$ with 
-  $\val[\primeit]{}{} \order \val[\doubleprimeit]{}{}$.
+  (\val[\primeit]{}{1}, \val[\secondit]{}{})$ with 
+  $\val[\primeit]{}{} \order \val[\secondit]{}{}$.
 
@@
   \goesto{a \cap P_1, \val[\doubletilde]{}{1}}
-  (q_1', \val[\primeit]{}{1}, q, \val[\doubleprimeit]{}{})
+  (q_1', \val[\primeit]{}{1}, q, \val[\secondit]{}{})
   $ in $\semopen{(\IMextend{\Gamma_1}{P_1})(\cB)}$.
@@
   \goesto{a \cap P_2, \val[\doubletilde]{}{2}}
-  (q_2', \val[\primeit]{}{2}, q, \val[\doubleprimeit]{}{})
+  (q_2', \val[\primeit]{}{2}, q, \val[\secondit]{}{})
   $ in $\semopen{(\IMextend{\Gamma_2}{P_2})(\cB)}$.

### 2018-10-11 2018-Arch-pNets/arch-pNets.tex
Arch-pNet paper: Updated the the Failure Monitor example (Fig. 1) and the explanation following the def of components

@@
 \usepackage{caption}
-\usepackage{xifthen}
 \usepackage{stmaryrd} % double brackets (\llbracket, \rrbracket)
@@
 
-The model in \fig{schema:ArchFailure:BIP} has three components.  The
-component $\NameOprnd$ is an \emph{operand} of the architecture, \ie
-it only has its interface defined: $(\emptyset, \{\PortFinish,
-\PortResume, \PortFail\}, \export[\emptyset])$, with
-$\export[\emptyset](p) = \emptyset$, for all $p \in \{\PortFinish,
-\PortResume, \PortFail\}$.  The other two components, $\NameCtrl$ and
-$\NameTimer$, are \emph{coordinators}\mdash they are specified
-completely, including the states and transitions defining their
-\emph{behaviour}.  Transitions are labelled with the ports of the
+The model in \fig{schema:ArchFailure:BIP} has two components:
+%% The
+%% component $\NameOprnd$ is an \emph{operand} of the architecture, \ie
+%% it only has its interface defined: $(\emptyset, \{\PortFinish,
+%% \PortResume, \PortFail\}, \export[\emptyset])$, with
+%% $\export[\emptyset](p) = \emptyset$, for all $p \in \{\PortFinish,
+%% \PortResume, \PortFail\}$.  
+%% The other two components,
+%
+$\NameCtrl$ and $\NameTimer$, with interfaces
+\[\bigl(
+\{\mathit{zone}\},
+\{\PortReset, \PortFail, \PortResume, \PortTO\},
+\export[\NameCtrl]
+\bigr)\]
+and
+\[\bigl(
+\{t, z\},
+\{\PortTick, \PortCancel, \PortTO\},
+\export[\NameTimer]
+\bigr)\]
+%
+respectively, where $\export[\NameCtrl](\PortFail) =
+\{\mathit{zone}\}$ and $\export[\NameCtrl](p) = \emptyset$, for all
+other ports $p$; $\export[\NameTimer](\PortTick) = \{t, z\}$ and
+$\export[\NameTimer](p) = \emptyset$, for all other ports $p$.
+Variable $t$ is implicitly assumed to be an integer.  Variables $z$
+and $\mathit{zone}$ are implicitly assumed to be integer intervals of
+the form $[l,u]$.  For both types, we also implicitly assume the
+natural ordering: increasing integers and interval inclusion.
+
+%% are \emph{coordinators}\mdash they are specified
+%% completely, including the states and transitions defining their
+%% \emph{behaviour}.
+Component \emph{behaviour} is defined by states ($\cstate{0},
+\cstate{1}, \cstate{2}$, for $\NameCtrl$, and $\tstate{0}$, for
+$\NameTimer$) and transitions.
+%
+Transitions are labelled with the ports of the
 corresponding components, Boolean guards and update assignments on local
-variables.  For instance, the loop transition $\tstate{1}
-\goesto{\PortTick, \GuardTick[], \TimerUpd[]} \tstate{1}$ in the
+variables.  For instance, the loop transition $\tstate{0}
+\goesto{\PortTick, \GuardTick[], \TimerUpd[]} \tstate{0}$ in the
 $\NameTimer$ component is labeled by the port $\PortTick$, it can be
 fired only when the current value of the local variable $t$ is less
-than $z.u$, where $z = [l, u]$ is a local variable representing an
-interval.  Upon firing, this transition increments the value of $t$ by
-$1$.  The guard and update assignment of the transition $\tstate{1}
-\goesto{\PortResume} \tstate{0}$ are omitted.  The default values are
-the constant predicate $\true$ and the empty assignment {\emptyassign}
-%$\mathit{skip}$ operator
-respectively.  The initial states \tstate{0} and \cstate{0}, and valuations $\val{0}{\NameTimer} = \{z
-\mapsto \topinterval, t \mapsto 0\}$ and $\val{0}{\NameCtrl} =
+than $z.u$.
+%% , where $z = [l, u]$ is a local variable representing an
+%% interval
+Upon firing, this transition increments the value of $t$ by $1$.  The
+guards and update assignments of the transitions of $\NameCtrl$ are
+omitted.  The default values are the constant predicate $\true$ and
+the empty assignment {\emptyassign}, respectively.  The initial states
+\tstate{0} and \cstate{0}, and valuations $\val{0}{\NameTimer} = \{t
+\mapsto 0, z \mapsto \topinterval\}$ and $\val{0}{\NameCtrl} =
 \{\mathit{zone} \mapsto [\mathrm{Min}, \mathrm{Max}]\}$ are shown by
 incoming arrows $\goesto{\TimerInit[]} \tstate{0}$ and
-$\goesto{\IntervalInit[]} \cstate{0}$, respectively.  The constants
-$\mathrm{Min}$ and $\mathrm{Max}$ are the parameters of the
-architecture.
+$\goesto{\IntervalInit[]} \cstate{0}$, respectively.\footnote{%
+%
+  We use $\topinterval$ to denote the top interval in the inclusion
+  order, \ie $(-\infty, +\infty)$.
+%
+} The constants $\mathrm{Min}$ and $\mathrm{Max}$ are the parameters
+of the architecture.
 %\noteLH{It looks like Max is in zone, I do not understand}

### 2018-10-11 2016-Weak-FH-Bisim/WeakBisim.tex

@@
 
-We can rewrite a weak open transition  $ \OTWeakarrow {\alpha}$ as a sequence of open transitions $(\OTarrow{\tau})\!* (\OTarrow{\alpha})(\OTarrow{\tau})* $.
+We can rewrite a weak open transition  $ \OTWeakarrow {\alpha}$ as a sequence of open transitions $(\OTarrow{\tau})^* (\OTarrow{\alpha})(\OTarrow{\tau})^* $.
 
@@
     \WT>$ be the
-weak open automata derived from $A$.  \\
+weak open automata derived from $A$.  The two following statements are equivalent
 %For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
-There exist  sets of $\beta^1_i$, $\beta^2_i$, and $\beta^3_i$, $\Pred^1_i$, $\Pred^3_i$, $\Post^1_i$, and  $\Pred^2$, $\Post^2$ s.t.:
+\begin{enumerate}
+\item Either $   
+\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'$; or \\ 
+there exist   $\set{\beta^1}_i$, $\set{\beta^2_i}$, and $\set{\beta^3_i}$, $\Pred^1_i$, $\Pred^3_i$, $\Post^1_i$, and  $\Pred^2$, $\Post^2$ s.t.:
 \begin{mathpar}
@@
 %\inferrule 
-\Bigg(\forall i \in [0\ldots n].\openrule
+\forall i \in [0\ldots n].\openrule
     {
@@
          {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
-\Bigg)        
-       \bigvee\\   
- \Big(\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
  \end{mathpar}
-If only if there exist $\set{\gamma}$, $\Pred$, $\Post$ s.t.
+\item  there exist $\set{\gamma}$, $\Pred$, $\Post$ s.t.
  \begin{mathpar}
@@
 
+\end{enumerate}
 \end{lemma}
@@
 \end{mathpar}
- such that  $\forall x, \{j\in J_1|\gamma_j\neq\emptyset\}=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
+ such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
  and  \\
@@
 Sketch for discussion.\\
-
-1) By lemma \ref{lem-rel-OT-WOT} we have:
-
+Definition 14 implies definition above
+
+WE SUPPOSE DEF 14, AND 
+ \begin{mathpar}
+     \openrule
+         {
+           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
+         {s \OTWeakarrow {\alpha} s'}
+
+\end{mathpar}
+
+we want
  \begin{mathpar}
@@
          {t \OTWeakarrow {\alpha_x} t_x}
+\end{mathpar}
+with the side conditions ....
+
+1) By lemma \ref{lem-rel-OT-WOT} we have:
+
+\begin{mathpar}
+     \openrule
+         {
+           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
+         {s \OTWeakarrow {\alpha} s'}
          \implies
@@
  \end{mathpar}
-2) From Definition \ref{def-Weak-bisim} we have:
+
+2) on the alpha we apply def 14: From Definition \ref{def-Weak-bisim} we have:
 

### 2018-10-17 2018-Arch-pNets/arch-pNets.tex
Arch-pNets paper: started the encoding section: Sub-section 1: no priority Sub-section 2: max progress Current state: no priority, encoding of components -- done, encoding of connectors explained on the running example -- formal ToDo; max progress -- ToDo

@@
 \usepackage{soul}
+\soulregister\cite7
+\soulregister\ref7
+\soulregister\pageref7
+\soulregister{\em}{0}
+\soulregister{\mdash}{0}
+\soulregister{\st}{7}
+\soulregister{\bf}{0}
+\soulregister{\fig}{7}
+\soulregister{\ie}{0}
+\soulregister{\etc}{0}
+\soulregister{\eg}{0}
+\soulregister{\wrt}{0}
+\soulregister{\resp}{0}
+\soulregister{\cf}{0}
+
+\soulregister{\cstate}{7}
+\soulregister{\tstate}{7}
+\soulregister{\goesto}{7}
+
 \usepackage[colorinlistoftodos,bordercolor=white]{todonotes}
@@
 \newcommand{\replaceSB}[2]{\replace[Replaced by Simon]{#1}{#2}}
+
+\usepackage{etoolbox}% http://ctan.org/pkg/etoolbox
+\newcommand{\tupleDeli}{(}
+\newcommand{\tupleDelii}{)}
+\newcommand{\setTupleDelims}[2][(]{
+  \renewcommand{\tupleDeli}{#1}%
+  \ifx#2\relax\else\renewcommand{\tupleDelii}{#2}\fi%
+}
+\newcommand{\tuple}[2][\ensuremath{,\allowbreak}]{%  
+  \def\nextitem{\def\nextitem{#1}}% Separator
+  \renewcommand*{\do}[1]{\nextitem ##1}% How to process each item
+  \tupleDeli\docsvlist{#2}\tupleDelii% Process list
+}
+
+\newcommand{\pNetTuple}[2][\ensuremath{,\allowbreak}]{%
+  \setTupleDelims[\mylangle]{\myrangle}%
+  \tuple[#1]{#2}%
+}
 
@@
 \newcommand{\setdef}[2]{\ensuremath{\{{#1}\,|\,{#2}\}}}
-\newcommand{\setdefb}[2]{\ensuremath{\bigl\{{#1}\,\bigl|\,{#2}\bigr.\bigr\}}}
+\newcommand{\bsetdef}[2]{\ensuremath{\bigl\{{#1}\,\bigl|\,{#2}\bigr.\bigr\}}}
 \newcommand{\Setdef}[2]{\ensuremath{\Big\{{#1}\,\Big|\,{#2}\Big\}}}
-\newcommand{\goesto}[2][]{\ensuremath{\xrightarrow[#1]{#2}}}
-\newcommand{\notgoesto}[2][]{\ensuremath{\not\xrightarrow[#1]{\ \,#2}}}
+\newcommand{\goesto}[2][]{\ensuremath{\xrightarrow[{#1}\relax]{#2}}}
+\newcommand{\notgoesto}[2][]{\ensuremath{\not\xrightarrow[{#1}\relax]{\ \,#2}}}
 \newcommand{\non}[1]{\ensuremath{\overline{#1}}}
@@
 \newcommand{\noop} {\ensuremath{\emptyset}} % \mathsf{skip}
+\newcommand{\init} {\ensuremath{\mathsf{init}}}
 
@@
 \newcommand{\val}[3][]{\ensuremath{#1{\sigma}^{#2}_{#3}}}
-\newcommand{\emptyassign}{\noop}
 
@@
 \newcommand{\secondit}[1]{#1''}
+
+\newcommand{\twosynch}{%
+  \ensuremath{\bullet\!\!\!-\!\!\!-\!\!\!-\!\!\!\bullet}}
+\newcommand{\synchtrig}{%
+  \ensuremath{\bullet\!\!\!-\!\!\!-\!\!\!\blacktriangleleft}}
+\newcommand{\trigsynch}{%
+  \ensuremath{\blacktriangleright\!\!\!-\!\!\!-\!\!\!\bullet}}
+\newcommand{\twotrig}{%
+  \ensuremath{\blacktriangleright\!\!\!-\!\!\!-\!\!\!\blacktriangleleft}}
 
@@
 \newcommand{\expmix}{\wedge}
+
+\newcommand{\addspace}[1]{#1 }
+\newcommand{\nopri}[1][]{\ensuremath{\mathit{pNet}%
+    \ifx#1\relax\else(#1)\fi}}
+\newcommand{\maxprog}[1][]{\ensuremath{\mathit{pNet}_\mu%
+    \ifx#1\relax\else(#1)\fi}}
+
+\newcommand{\partition}{\cD}
 
@@
 to denote the set of \emph{variable assignments}.}  We use the symbol
-$\emptyassign$ to denote the empty assignment, \ie an assignment with
+$\noop$ to denote the empty assignment, \ie an assignment with
 $I = \emptyset$.
@@
 \order)$ comprises both the unordered set of Booleans $\sB =
-(\{\true, \false\}, \emptyset)$ and the naturally ordered one
-$\sB^< = (\{\true, \false\}, \{\false < \true\})$, and
+\tuple{\{\true, \false\}, \emptyset}$ and the naturally ordered one
+$\sB^< = \tuple{\{\true, \false\}, \{\false < \true\}}$, and
 similarly for integer and real numbers; as well as the set of
@@
 \data$, we denote \[\valdiff{\val{1}{}}{\val{2}{}} \bydef{=}
-\setdefb{v \in V}{\val{1}{}(v) \neq \val{2}{}(v)}\] the set of
+\bsetdef{v \in V}{\val{1}{}(v) \neq \val{2}{}(v)}\] the set of
 variables that are assigned different values by the two
@@
 %
-$\NameCtrl$ and $\NameTimer$, with interfaces
+$\NameTimer$ and $\NameCtrl$, with interfaces
+\[\bigl(
+\{t, z\},
+\{\PortTick, \PortCancel, \PortTO\},
+\export[\NameTimer]
+\bigr)\,,
+\qquad
+\export[\NameTimer](p) =
+\begin{cases}
+  \{t, z\}, & \text{if } p = \PortTick,\\
+  \emptyset, & \text{otherwise}
+\end{cases}
+\]
+and
 \[\bigl(
@@
 \export[\NameCtrl]
-\bigr)\]
-and
-\[\bigl(
-\{t, z\},
-\{\PortTick, \PortCancel, \PortTO\},
-\export[\NameTimer]
-\bigr)\]
-%
-respectively, where $\export[\NameCtrl](\PortFail) =
-\{\mathit{zone}\}$ and $\export[\NameCtrl](p) = \emptyset$, for all
-other ports $p$; $\export[\NameTimer](\PortTick) = \{t, z\}$ and
-$\export[\NameTimer](p) = \emptyset$, for all other ports $p$.
+\bigr)\,,
+\quad
+\export[\NameCtrl](p) =
+\begin{cases}
+  \{\mathit{zone}\}, & \text{if } p = \PortFail,\\
+  \emptyset, & \text{otherwise}
+\end{cases}
+\]
+%
+respectively. %% , where $\export[\NameCtrl](\PortFail) =
+%% \{\mathit{zone}\}$ and $\export[\NameCtrl](p) = \emptyset$, for all
+%% other ports $p$; $\export[\NameTimer](\PortTick) = \{t, z\}$ and
+%% $\export[\NameTimer](p) = \emptyset$, for all other ports $p$.
 Variable $t$ is implicitly assumed to be an integer.  Variables $z$
@@
 %% \emph{behaviour}.
-Component \emph{behaviour} is defined by states ($\cstate{0},
-\cstate{1}, \cstate{2}$, for $\NameCtrl$, and $\tstate{0}$, for
+Component \emph{behaviour} is defined by states ($\{\cstate{0},
+\cstate{1}, \cstate{2}\}$, for $\NameCtrl$; $\{\tstate{0}\}$, for
 $\NameTimer$) and transitions.
@@
 guards and update assignments of the transitions of $\NameCtrl$ are
-omitted.  The default values are the constant predicate $\true$ and
-the empty assignment {\emptyassign}, respectively.  The initial states
+omitted.  The default values are the constant predicate $\true$ (true) and
+the empty assignment {\noop}, respectively.  The initial states
 \tstate{0} and \cstate{0}, and valuations $\val{0}{\NameTimer} = \{t
@@
   \label{defn:comp:semantics}
-  The \emph{open semantics} of a component $B = (Q, q^0, V,
-  \val{0}{}, P, \export, \goesto{})$ is given by the LTS denoted $\semopen{B} = (S,
-  s^0, \goesto{})$, where $S = Q \times \valuations{V}$, $s^0 =
-  (q^0, \val{0}{})$ and $\goesto{}$ is the minimal transition
+  The \emph{open semantics} of a component $B = \tuple{Q, q^0, V,
+  \val{0}{}, P, \export, \goesto{}}$ is given by the LTS denoted $\semopen{B} = \tuple{S,
+  s^0, \goesto{}}$, where $S = Q \times \valuations{V}$, $s^0 =
+  \tuple{q^0, \val{0}{}}$ and $\goesto{}$ is the minimal transition
   relation satisfying the rule
@@
   \label{defn:im:sem}
-  The \emph{composition} of a finite set of components $\cB = (Q_i,
-  q^0_i, V_i, \val{0}{i}, P_i, \export[i], \goesto{})^{i \in I}$ with
-  the interaction model $\Gamma$ over $(V, P, \export)$ (as in \defn{im})
-  is the component $\Gamma(\cB) = (Q, q^0, V, \val{0}{}, P,
-    \export, \goesto{})$, where
+  The \emph{composition} of a finite set of components $\cB = \tuple{Q_i,
+  q^0_i, V_i, \val{0}{i}, P_i, \export[i], \goesto{}}^{i \in I}$ with
+  the interaction model $\Gamma$ over $\tuple{V, P, \export}$ (as in \defn{im})
+  is the component $\Gamma(\cB) = \tuple{Q, q^0, V, \val{0}{}, P,
+    \export, \goesto{}}$, where
 %
@@
 
-For instance, in \fig{schema:ArchFailure:BIP}, the two ports
+\todoSB{Update this}
+\hl{For instance, in \fig{schema:ArchFailure:BIP}, the two ports
 $\NameTimer.\PortStart$ and $\NameCtrl.\PortFail$ are always
@@
 where they are both synchrons.  In particular, this means that
-whenever the transition $\cstate{0} \goesto{\PortFail} \cstate{1}$ is
-fired, so is the transition $\tstate{0} \goesto{\PortStart,
-  \TimerInit[]} \tstate{1}$, initialising the timer.  The binary
-connector $\NameTimer.\PortStart \bullet\!\!\!-\!\!\!-\!\!\!\bullet
+whenever the transition \cstate{0} \goesto{\PortFail} \cstate{1} is
+fired, so is the transition \tstate{0} \goesto{\PortStart,
+  \TimerInit[]} \tstate{1}, initialising the timer.  The binary
+connector $\NameTimer.\PortStart \twosynch
 \NameCtrl.\PortFail$ is a sub-connector of a hierarchical connector,
@@
 port $\NameOprnd.\PortFail$ can fire alone, forming a singleton
-interaction.
+interaction.}
 
@@
   We write $\alpha \prec_\pi \beta$ for $(\alpha, \beta) \in \pi$ and 
-  denote $\filter{\alpha} \bydef{=} \setdefb{\beta \in (2^P \times
+  denote $\filter{\alpha} \bydef{=} \bsetdef{\beta \in (2^P \times
     \guards{V} \times \updates{V})}{\alpha \prec_\pi \beta}$ the set of
@@
   The application of a priority model $\pi$ over $(V, P, \export)$
-  to a component $B = (Q, q^0, V, \val{0}{}, P, \export, \goesto{})$
-  is the component $\pi(B) = (Q, q^0, V, \val{0}{}, P, \export,
-  \goesto[\pi]{})$, where $\goesto[\pi]{}$ is the minimal transition
+  to a component $B = \tuple{Q, q^0, V, \val{0}{}, P, \export, \goesto{}}$
+  is the component $\pi(B) = \tuple{Q, q^0, V, \val{0}{}, P, \export,
+  \goesto[\pi]{}}$, where $\goesto[\pi]{}$ is the minimal transition
   relation satisfying the rule
@@
   where $\filter[q]{\alpha} \bydef{=} %% \filter{\alpha} \cap
-  %% \setdefb{\beta \in (2^P \times \guards{V} \times \updates{V})}
+  %% \bsetdef{\beta \in (2^P \times \guards{V} \times \updates{V})}
   \setdef{\beta \in \filter{\alpha}}{q \goesto{\beta}}$.
@@
   \label{defn:arch}
-  An \emph{architecture} is a tuple $A = (\cC, V_A, P_A, \export[A], \Gamma)$,
-  where $\cC$ is a finite set of \emph{coordinating components}
+  An \emph{architecture} is a tuple $A = \tuple{\cC, V_A, P_A,
+    \export[A], \Gamma}$, where
+%  
+  \begin{itemize}
+\item
+  $\cC$ is a finite set of \emph{coordinating components}
   with pairwise disjoint sets of ports and variables, such that
@@
 %
+  ports in $P_A \setminus \bigcup_{C \in \cC} P_C$, which do not
+  belong to any of the coordinating components are called
+  \emph{dangling};
+
+\item
   $\export[A] : P_A \rightarrow 2^{V_A}$ is an export function, such
@@
   P_C$ and $\export[A](p) \subseteq V_A \setminus \bigcup_{C \in \cC}
-  V_C$ for any $p \in P_A \setminus \bigcup_{C \in \cC} P_C$; and
-%
+  V_C$ for any dangling port $p$; and
+
+\item
   $\Gamma \subseteq 2^{P_A} \times \guards{V_A} \times \exprs{V_A}$
-  is an interaction model over \hl{$(V_A, P_A, \export[A])$}.
+  is an interaction model over $(V_A, P_A, \export[A])$.
+  \end{itemize}
+
 \end{definition}
@@
   \label{defn:arch:application}
-  Let $A = (\cC, V_A, P_A, \export[A], \Gamma)$ be an architecture and let $\cB$
+  Let $A = \tuple{\cC, V_A, P_A, \export[A], \Gamma}$ be an architecture and let $\cB$
   be a set of components, such that
@@
     \IMextend{\Gamma}{P} &\bydef{=}
-    \setdefb{
+    \bsetdef{
       (a \cup a', g, e)
@@
     &= 
-    \setdefb{
+    \bsetdef{
       (a, g, e)
@@
   \label{defn:arch:composition}
-  Let $A_i = (\cC_i, V_{A_i}, P_{A_i}, \export[A_i], \Gamma_i)$, for $i = 1,2$,
+  Let $A_i = \tuple{\cC_i, V_{A_i}, P_{A_i}, \export[A_i], \Gamma_i}$, for $i = 1,2$,
   be two architectures.  The \emph{composition} of $A_1$ and
-  $A_2$ is the architecture $A_1 \arcomp A_2 = (\cC_1 \cup \cC_2,
-  V_{A_1} \cup V_{A_2}, P_{A_1} \cup P_{A_2}, \export[A_1] \cup \export[A_2], \Gamma)$, where
+  $A_2$ is the architecture $A_1 \arcomp A_2 = \tuple{\cC_1 \cup \cC_2,
+  V_{A_1} \cup V_{A_2}, P_{A_1} \cup P_{A_2}, \export[A_1] \cup \export[A_2], \Gamma}$, where
 %
@@
     \label{eq:arch:composition}
-    \Gamma = \setdefb{
+    \Gamma = \bsetdef{
       (a, g^1 \land g^2, e^1 \expmix e^2) 
@@
   \label{defn:impose}
-  Let $A = (\cC, P_A, V_A, \export[A], \Gamma)$ be an architecture; let $\cB$
+  Let $A = \tuple{\cC, P_A, V_A, \export[A], \Gamma}$ be an architecture; let $\cB$
   be a set of components and $\Phi$ an initial property of
@@
 %
-  Consider two architectures $A_i = (\cC_i, V_{A_i}, P_{A_i},
-  \export[A_i], \Gamma_i)$, for $i = 1,2$.
+  Consider two architectures $A_i = \tuple{\cC_i, V_{A_i}, P_{A_i},
+  \export[A_i], \Gamma_i}$, for $i = 1,2$.
 %
@@
   \label{thm:combining}
-  Let $\cB$ be a set of components; let $A_i = (\cC_i, V_{A_i},
-  P_{A_i}, \export[A_i], \Gamma_i)$, for $i = 1,2$, be two upwards compatible architectures
+  Let $\cB$ be a set of components; let $A_i = \tuple{\cC_i, V_{A_i},
+  P_{A_i}, \export[A_i], \Gamma_i}$, for $i = 1,2$, be two upwards compatible architectures
   enforcing on $\cB$ the properties $\Phi_1$ and $\Phi_2$
@@
 
+We will define the encoding of BIP architectures into pNets by
+associating to each architecture \emph{and a partition of its dangling
+  ports} the corresponding pNet.  Notice that the addition of a
+partition of dangling ports is a matter of convenience, since one can
+use a trivial partition comprising only one complete set of dangling
+ports.
+
+Let $A = \tuple{\cC, V_A, P_A, \export[A], \Gamma}$ be an
+architecture.  For each $C \in \cC$, let $C = \tuple{Q_C, q^0_C, V_C,
+  \val{0}{C}, P_C, \export[C], \goesto{}}$.  Finally, let $\partition
+\subseteq 2^{P_A}$ be a partition of the set of dangling ports of $A$,
+\ie $\bigcup_{D \in \partition} D = P_A \setminus \bigcup_{C \in \cC}
+P_C$ and $D_1 \cap D_2 = \emptyset$, for any two distinct $D_1, D_2
+\in \partition$.  In particular, as mentioned above, one can consider
+the trivial partition $\partition \bydef{=} \{P_A \setminus \bigcup_{C
+  \in \cC} P_C\}$.
+
+Below, for the sake of clarity, we start by presenting in
+\secn{enc:nopri} the encoding of $A$ into pNets without accounting for
+any priority model (see \secn{components}).  Then, in
+\secn{enc:maxprog}, we slightly modify this encoding to include the
+implicitly assumed maximal progress priority.
+
+%****************************************************************
+\subsection{Encoding without the priority model}
+\label{secn:enc:nopri}
+
+Recall that $\Gamma$ is an interaction model over the interface
+$\tuple{V_A, P_A, \export[A]}$, \ie these interface elements are
+implicitly involved in the definition of $\Gamma$.
+
+\paragraph{Encoding the coordinators} We define the
+mapping $\nopri$ as $\nopri[A, \partition] \bydef{=}
+\pNetTuple{(\nopri[C])^{C \in \cC}, \partition, \nopri[\Gamma]}$,
+where, for each $C \in \cC$, the encoding $\nopri[C]$ is a pLTS
+$\pNetTuple{S, s_0, \goesto[{\nopri[C]}]{}}$, such that
+%
+\begin{itemize}
+\item $s_0 \not\in Q_C$ is fresh and $S = Q_C \cup \{s_0\}$,
+\item $\vars(s) = V_C$, for all $s \in Q_C$, and $\vars(s_0) =
+  \emptyset$,
+\item the transition relation $\goesto[{\nopri[C]}]{}$ is defined as
+  the union of three sets of transitions:
+%
+  \begin{multline}
+    \label{eq:nopri:trans}
+    \goesto[{\nopri[C]}]{} \bydef{=}
+    \bsetdef{\tuple{s, a(\true), g, u, s'}}{
+      \tuple{s, a, g, u, s'} \in \goesto{}}
+    \\    
+    \cup
+    \bsetdef{\tuple{s, a(\false), \true, \noop, s}}{
+      s \in Q_C, a \in P_C}
+    \\
+    \cup
+    \bigl\{(s_0, \init, \true, \mathit{init}, q^0_C)\bigr\}
+    \,,
+  \end{multline}
+%
+  where \noteSB{Can probably write directly $\overline{V_C := \val{0}{C}}$, in which case no need to intrudce $\mathit{init}$.}\hl{$\mathit{init} = \bigl(x := \val{0}{C}(x)\bigr)^{x \in V_C}$}.
+\end{itemize}
+
+\noteSBin{Eric uses some kind of initialisation predicate in
+  Fig.~\ref{schema:ArchFailure:BIP}.  I do not quite understand how
+  this works, so I used a new initial state with explicit
+  initialisation.}
+
+Intuitively, we 1)~introduce a fresh initial state with an additional
+$\init$ transition that initialises all the variables to those defined
+by the initial valuation $\val{0}{C}$ of $C$ and 2)~associate an
+additional Boolean value to each port, with original transitions of
+$C$ marked by $\true$ and additional loop transitions marked by
+$\false$.
+
+\Fig{enc:nopri} shows the encoding of the Failure Monitor
+architecture, including the encodings of the two coordinators, \ie
+$\nopri[\NameTimer]$ and $\nopri[\NameCtrl]$.  Notice that the
+encoding in the figure is slightly optimised: some of the ports do not
+have an associated Boolean value, nor the additional loop transitions.
+We will explicitate this optimisation once we have defined the
+encoding of the interaction model.
+
+\begin{figure*}[t]
+  \fbox{%
+  \includegraphics[width=\textwidth]{BIPspec-ArchFailureTimerMax-v4-no-pri}}
+  \caption{Encoding of the Failure Monitor architecture
+    (\fig{schema:ArchFailure:BIP}) as an open pNet (without the
+    priority model) \hl{\bf (Error in the picture: First two positions in the synchronisation vectors must be transposed)}}
+  \label{fig:enc:nopri}
+\end{figure*}
+
+\paragraph{Encoding the interaction model}
+First of all, recall that $\nopri[A, \partition ] \bydef{=}
+\pNetTuple{(\nopri[C])^{C \in \cC}, \partition, \nopri[\Gamma]}$.
+Thus, the holes in the resulting pNet are indexed by the elements of
+partition \partition.  For the encoding of our running example, we
+take $\partition = \bigl\{\{\PortFail, \PortResume\},\{\PortAsk,
+\PortReset\}\bigr\}$.  This corresponds to the intuition that the
+dangling ports {\PortFail} and {\PortResume} correspond to the
+monitored events, whereas {\PortAsk} and {\PortReset} correspond to
+the actions provided by the ``environment'' (other components of the
+system) that are triggered in case of a persistent failure.  Similarly
+to the encoding of the corrdinators, in the synchronisation vectors of
+\nopri[\Gamma], we will associate Boolean values to the actions
+corresponding to these ports.
+
+The encoding of the interaction model is based on its representation
+as a set of connectors. \noteSB{A legitimate question is whether we
+  actually need to do this, instead of listing explicitly the
+  individual interactions, then associating a synchronisation vector
+  to each one of them?  One of the factors is the encoding
+  pNets$\rightarrow$SAT: is it better to have more or fewer SVs if the
+  price is additional Boolean variables?  The other factor might be
+  the facility of maximal progress encoding\mdash TBC.  Traceability.
+  Anything else?  }Indeed, as illustrated by the Failure Monitor
+architecture in \fig{schema:ArchFailure:BIP}, each connector can
+define several allowed interactions, depending on its hierarchical
+structure and port and node syncrhon/trigger typings.  For instance,
+the connector {\NameTimer.\PortTick \trigsynch (\PortFail \trigsynch
+  \NameCtrl.\PortFail)} defines three interactions (observe that
+$\topinterval + \NameTimer.t = \topinterval$ and $\NameTimer.z \cap
+\topinterval = \NameTimer.z$):\noteSB{Move this to \secn{components}?}
+%
+\begin{align*}
+  &\bigl(\{\NameTimer.\PortTick\},
+  &&\true, 
+  &&\NameTimer.z := \NameTimer.z\bigr)
+  \\
+  &\bigl(\{\NameTimer.\PortTick, \PortFail\},
+  &&\true,
+  &&\NameTimer.z := \NameTimer.z\bigr)
+  \\
+  &\bigl(\{\NameTimer.\PortTick, \PortFail, \NameCtrl.\PortFail\},
+  &&\true,
+  &&\NameTimer.z := \NameTimer.z \cap (\NameCtrl.\mathit{zone} + \NameTimer.t)\bigr)
+\end{align*}
+
+In order to encode these using only one synchronisation vector, we use
+the additional Boolean values associated to each port by the encoding
+of coordinator components.  We observe that the three ports in this
+connector form a ``causality chain'': {\NameCtrl.\PortFail} can only
+participate in the interaction if the dangling port {\PortFail}
+participates, which in turn can only participate if
+{\NameTimer.\PortTick} does so.  These dependencies can be rewritten
+as Boolean implications $\NameCtrl.\PortFail \Rightarrow \PortFail$
+and $\PortFail \Rightarrow \NameTimer.\PortTick$.  However, notice
+that, within the scope of this connector, {\NameTimer.\PortTick}
+participates in all the interactions, meaning that the latter
+implication is a tautology and can be discarded.  Thus, we obtain the
+synchronisation vector SV0 shown in \fig{enc:nopri}, where $b_0$ and
+$b_1$ are the Boolean values associated to the actions encoding the
+ports {\PortFail} and {\NameCtrl.\PortFail}, $\alpha_0$ is a fresh
+action name.  The guard $b_1 \Rightarrow b_0$ encodes the causal
+relation among ports {\NameCtrl.\PortFail} and {\PortFail}.  Notice
+that, in our encoding, all three ports are present in the
+synchronisation vector.  Non-participation of a port corresponds to
+firing the loop transition marked by \false.  \Fig{enc:nopri} shows
+the four synchronisation vectors SV0\ndash SV3 corresponding to the
+connectors in \fig{schema:ArchFailure:BIP} and an additional vector
+SV4, synchronising the {\init} transitions of the two pLTSs.
+
+%****************************************************************
+\subsection{Encoding with the maximal progress priority model}
+\label{secn:enc:maxprog}
+
 %****************************************************************
@@
   \label{lem:onlyone}
-  Let $A = (\cC, V_A, P_A, \export[A], \Gamma)$ be an architecture and denote
+  Let $A = \tuple{\cC, V_A, P_A, \export[A], \Gamma}$ be an architecture and denote
   by $\Gamma_\cC \bydef{=}
@@
   the projection of $\Gamma$ onto the coordinating components of
-  $A$.  Consider the architecture $A' = (\{C'\}, V_A, P_A, \export[A],
-  \Gamma)$, where $C' = \Gamma_\cC(\cC)$.  For any set of
+  $A$.  Consider the architecture $A' = \tuple{\{C'\}, V_A, P_A, \export[A],
+  \Gamma}$, where $C' = \Gamma_\cC(\cC)$.  For any set of
   components $\cB$, satisfying the conditions of
@@
   \label{lem:onestep}
-  Let $\cB$ be a set of components; let $A_i = (\{C_i\}, V_{A_i},
-  P_{A_i}, \export[A_i], \Gamma_i)$, for $i = 1,2$, be two upwards compatible architectures
+  Let $\cB$ be a set of components; let $A_i = \tuple{\{C_i\}, V_{A_i},
+  P_{A_i}, \export[A_i], \Gamma_i}$, for $i = 1,2$, be two upwards compatible architectures
   with one coordinator each, applicable to $\cB$.  Denote

### 2018-10-18 2018-Arch-pNets/arch-pNets.tex
Reading simon;s text : more details on the generation of synch vectors

@@
 $\init$ transition that initialises all the variables to those defined
-by the initial valuation $\val{0}{C}$ of $C$ and 2)~associate an
-additional Boolean value to each port, with original transitions of
-$C$ marked by $\true$ and additional loop transitions marked by
+by the initial valuation $\val{0}{C}$ of $C$ and 2)~define a pNet action algebra that associates, as action parameter, an
+additional Boolean value to each port, 3)~create pNet transitions that reflect the original transitions of
+$C$ with $\true$ as parameter and 4)~create additional loop transitions marked by
 $\false$.
@@
 \PortReset\}\bigr\}$.  This corresponds to the intuition that the
-dangling ports {\PortFail} and {\PortResume} correspond to the
-monitored events, whereas {\PortAsk} and {\PortReset} correspond to
+dangling ports {\PortFail} and {\PortResume} will be provided by a monitoring component, whereas {\PortAsk} and {\PortReset} correspond to
 the actions provided by the ``environment'' (other components of the
 system) that are triggered in case of a persistent failure.  Similarly
-to the encoding of the corrdinators, in the synchronisation vectors of
+to the encoding of the coordinators, in the synchronisation vectors of
 \nopri[\Gamma], we will associate Boolean values to the actions

### 2018-10-18 2016-Weak-FH-Bisim/WeakBisim.tex
Proof of corollary V1

@@
        	\Leftrightarrow % we changed = 
-       	 \Pred\!'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}} $\\
+       	 \Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}} $\\
 
@@
 
-\TODO{Lemma revu mais convaincant...}
-
 \begin{lemma}
@@
 
-\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau transitions such $n_1=n+m+1$, hence by simplification we have (strictly speaking, by induction we might also have the case $\alpha=\tau\land\set \gamma=\emptyset\land \ldots$ but in this case, \WTUn\ allows us to obtain a similar redution with $n_1=1$):
+\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau transitions such $n_1=n+m+1$, hence by simplification we have (strictly speaking, by induction we might also have the case $\alpha=\tau\land\set \gamma=\emptyset\land \ldots$ but in this case, \WTUn\ allows us to obtain a similar reduction with $n_1=1$):
 \begin{mathpar}
@@
 \displaystyle{\Post= ({x^8_k\gets (e^8_k\subst {\Post^7})\subst{\biguplus_{i=0}^{n_2} \Post^6_i}})^{k\in K}}
-$
+$\\
 This concludes the inductive step, showing  that the decomposition expressed by the $\Leftarrow$ direction of the lemma is always possible. 
@@
    have:
-
 \begin{itemize}
@@
 \end{corollary}
+\TODO{Proof in progress}
 \begin{proof} 
-Sketch for discussion.\\
-Definition 14 implies definition above
-
-WE SUPPOSE DEF 14, AND 
+($\Rightarrow$) Firstly, we prove that Definition \ref{def-Weak-bisim} implies definition above.
+
+Suppose that for any open transition $OT$ in $\mathcal{T}_1$:
+ \begin{mathpar}
+     \openrule
+         {
+           \beta_j^{j\in J'_1},\Pred_{OT},\Post_{OT}}
+         {s \OTarrow {\alpha} s'}
+
+\end{mathpar}
+ there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
+ \begin{mathpar}
+    \openrule
+         {
+           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {t \OTWeakarrow {\alpha_x} t_x}
+\end{mathpar}
+ such that  $\forall x, \{j\in J'|\beta_j\neq\tau\}=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
+ and  \\
+ $\Pred \land \Pred_{OT}\\
+ \implies\!\!\!\displaystyle{\bigvee_{x\in X}}
+   \left(\forall j\in J_x. \vis{\beta_j}=\gamma_{jx}\Rightarrow \Pred_{OT_x}
+     \land \alpha\!=\!\alpha_x\land  
+     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
+
+and  suppose we have:
 \begin{mathpar}
@@
 \end{mathpar}
-
-we want
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {t \OTWeakarrow {\alpha_x} t_x}
-\end{mathpar}
-with the side conditions ....
-
-1) By lemma \ref{lem-rel-OT-WOT} we have:
-
+By using lemma \ref{lem-rel-OT-WOT} we have:
 \begin{mathpar}
@@
          \implies
-
- \Bigg(\forall i \in [0\ldots n].\openrule
+\bigg(\forall i \in [0\ldots n].\openrule
     {
        \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
-         {s^1_i \OTarrow {\tau} s^1_{i}} \in \mathcal{T} \quad \wedge
-\quad
-\openrule
-         {
-           \set{\beta^2},\Pred\,^2,\Post^2 }
+         {s^1_i \OTarrow {\tau} s^1_{i}} \in \mathcal{T}  \wedge
+
+\openrule
+         {
+           \beta_j^{J^2},\Pred\,^2,\Post^2 }
          {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
-\quad \wedge\\
+ \wedge
 \forall i \in [0\ldots m].\openrule
@@
          {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
-\Bigg) 
- \end{mathpar}
-
-2) on the alpha we apply def 14: From Definition \ref{def-Weak-bisim} we have:
-
-For each open transition $OT$ in $\mathcal{T}_1$:
- \begin{mathpar}
-     \openrule
-         {
-           \beta_j^{j\in J'},\Pred_{OT},\Post_{OT}}
-         {s \OTarrow {\alpha} s'}
-
+\bigg)
+\end{mathpar}
+The (\WTDeux)~ and (\WTTrois)~  rules can be applied repeatedly to produce:
+\begin{mathpar}
+%\inferrule{
+ \forall i \in [0\ldots n].\openrule
+    {
+       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
+         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}          \implies
+ \openrule
+         {
+           \set{\gamma_1},\Pred_1,\Post_1   }
+         {s \OTWeakarrow {\tau} s_1} \in\! \WT 
+\end{mathpar}
+where 
+\begin{mathpar}
+s=s^1_0 \wedge s^1_{n}\!=s_1,
+\displaystyle{\set{\gamma_1}=\mybigdotcup_{i=0}^{n} \vis{\set{\beta^1_i}}}, 
+\Pred_1\!=\!\bigwedge_{i=0}^{n}\Pred^1_i, \Post_1= \biguplus_{i=0}^{n} \Post_i^1\\
+\end{mathpar}
+And similarly, a series of $m$ open transitions can be simplified:
+\begin{mathpar}
+%\inferrule{
+\forall i \in [0\ldots m].\openrule
+         {
+           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\!\gets e^3_k})^{k\in K}    }
+         {s^3_i \OTarrow {\tau} s^3_{i+1}}\! \in\! \mathcal{T}       
+          \!\implies\!
+\openrule
+         {
+           \set{\gamma_3},\Pred_3, ({x_k\!\gets e_k})^{k\in K}}
+         {s_2 \OTWeakarrow {\tau} s'}\! \in\! \WT 
+\end{mathpar}
+where 
+\begin{mathpar}
+s_2=s^3_0 \wedge s^3_{m}\!=s',
+\displaystyle{\set{\gamma_3}=\mybigdotcup_{i=0}^{m} \vis{\set{\beta^3_i}}}, 
+\Pred_3\!=\!\bigwedge_{i=0}^{m}\Pred^3_i 
+%\Post_3= \biguplus_{i=0}^{n_1} \Post_i^1\\
+\end{mathpar}
+Concerning the middle open transition, by Definition \ref{def-Weak-bisim} we know that for each open transition $OT$ in $\mathcal{T}_1$:
+ \begin{mathpar}
+     \openrule
+         {
+           \beta_j^{J^2},\Pred\,^2,\Post^2 }
+         {s^2 \OTarrow {\alpha} s'^2} 
 \end{mathpar}
@@
 \end{mathpar}
- such that  $\forall x, \{j\in J'|\beta_j\neq\tau\}=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
- and  \\
- $\Pred \land \Pred_{OT}\\
+ such that  $\forall x,J^2=J_{x}, (s'^2,t_x|\Pred_{s'^2,t_x})\in \mathcal{R}$; 
+ and  \TODO{$\{j\in J^2|\beta_j\neq\tau\}$ useless} \\
+ $\Pred \land \Pred\,^2\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
@@
      \land \alpha\!=\!\alpha_x \land  
-     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
-
- 3) From Definition \ref{def:buildweakOT} we have:
+     \Pred_{s'^2,t_x}\subst{\Post^2}\subst{\Post_{OT_x}}\right)$
+
+\medskip
+
+On other hand, by applying (\WTTrois)~rule  on each  $\symb{WOT}_x$ we have:
 
@@
            \set{\gamma_1},\Pred_1,\Post_1   }
-         {s \OTWeakarrow {\tau} s_1} \in \WT
+         {s \OTWeakarrow {\tau} s_1} 
 \qquad
@@
          {
-           \set{\gamma_2},\Pred_2,\Post_2  }
-         {s_1 \OTWeakarrow {\alpha} s_2} \in \WT
+           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {t \OTWeakarrow {\alpha_x} t_x}
 \qquad
@@
            \set{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
-         {s_2 \OTWeakarrow {\tau} s'} \in\WT
+         {s_2 \OTWeakarrow {\tau} s'} 
 \\
-\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
+\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_{OT_x}})\subst{\Post_1}
 }
@@
          {
-           \set{\gamma_1}\dotcup \set{\gamma_2}\dotcup\set{\gamma_3},
+           \set{\gamma_1}\dotcup\gamma_{j x}^{j\in J_{x}} \dotcup\set{\gamma_3},
 		\Pred,
-				({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K} } 
-         {s \OTWeakarrow {\alpha} s'} \in\WT
-} \WTTrois
-\end{mathpar}
-
- \TODO{Trouver comment decrire la recurrence/fusionner les Pred}
+				({x_k\gets (e_k\subst {\Post_{OT_x}})\subst{\Post_1}})^{k\in K} } 
+         {s \OTWeakarrow {\alpha_x} s'} 
+} 
+ \end{mathpar}
+such that
+$s_1=t \wedge t_x=s_2$  \TODO{Attention les states; I'm not convinced}\\
+Therefore, we can deduce that:
+
+For any open transition $\symb{WOT}$ in $\WT_1$:
+ \begin{mathpar}
+     \openrule
+         {
+           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
+         {s \OTWeakarrow {\alpha} s'}
+
+\end{mathpar}
+ there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
+ \begin{mathpar}
+ {
+\openrule
+         {
+           \set{\gamma_1}\dotcup\gamma_{j x}^{j\in J_{x}} \dotcup\set{\gamma_3},
+		\Pred,
+				({x_k\gets (e_k\subst {\Post_{OT_x}})\subst{\Post_1}})^{k\in K} } 
+         {s \OTWeakarrow {\alpha_x} s'} 
+}     
+\end{mathpar}
+\TODO{Side Conditions to discuss}\\
+ such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
+ and  \\
+$\Pred \land \Pred_{OT}\\
+\displaystyle{\implies\!\!\! \bigvee_{x\in X}
+   \left( \forall j\in J_x.\gamma_j=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
+     \land \alpha\!=\!\alpha_x \land  
+     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)}$
+
+\noindent ($\Leftarrow$) Now, we prove that the definition above implies Definition \ref{def-Weak-bisim}.
+
+Suppose that for any weak open transition $\symb{WOT}$ in $\WT_1$:
+ \begin{mathpar}
+     \openrule
+         {
+           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
+         {s \OTWeakarrow {\alpha} s'}
+
+\end{mathpar}
+ there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
+ \begin{mathpar}
+    \openrule
+         {
+           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {t \OTWeakarrow {\alpha_x} t_x}
+\end{mathpar}
+ such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
+ and  \\
+$\Pred \land \Pred_{OT}\\
+\displaystyle{\implies\!\!\! \bigvee_{x\in X}
+   \left( \forall j\in J_x.\gamma_j=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
+     \land \alpha\!=\!\alpha_x \land  
+     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)}$
+
+and suppose that we have:
+\begin{mathpar}
+     \openrule
+         {
+           \beta_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
+         {s \OTarrow {\alpha} s'}
+
+\end{mathpar}
+
+By applying (\WTDeux)~rule we can directly deduce that we have:
+
+\begin{mathpar}
+     \openrule
+         {
+           \vis{\beta_j^{j\in J_1}},\Pred_{OT},\Post_{OT}}
+         {s \OTWeakarrow {\alpha} s'}
+
+\end{mathpar}
+
+Then by transitivity,   it is straightforward to  deduce that for any open transition $\symb{OT}$ in $\mathcal{T}_1$:
+ \begin{mathpar}
+     \openrule
+         {
+           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
+         {s \OTarrow {\alpha} s'}
+
+\end{mathpar}
+ there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
+ \begin{mathpar}
+    \openrule
+         {
+           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {t \OTWeakarrow {\alpha_x} t_x}
+\end{mathpar}
+ such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
+ and  \\
+$\Pred \land \Pred_{OT}\\
+\displaystyle{\implies\!\!\! \bigvee_{x\in X}
+   \left( \forall j\in J_x.\vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
+     \land \alpha\!=\!\alpha_x \land  
+     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)}$
 

### 2018-10-18 2018-Arch-pNets/arch-pNets.tex
Arch-pNet paper: minor change in Ludo's edits

@@
 \PortReset\}\bigr\}$.  This corresponds to the intuition that the
-dangling ports {\PortFail} and {\PortResume} will be provided by a monitoring component, whereas {\PortAsk} and {\PortReset} correspond to
+dangling ports {\PortFail} and {\PortResume} will be provided by a 
+monitored component, whereas {\PortAsk} and {\PortReset} correspond to
 the actions provided by the ``environment'' (other components of the

### 2018-10-18 2018-Arch-pNets/arch-pNets.tex
Arch-pNet paper: some modifications in response to comments by Ludo: Expanded the explanation of how the tick-fail-fail connector in the running example defines three interactions

@@
 $\init$ transition that initialises all the variables to those defined
-by the initial valuation $\val{0}{C}$ of $C$ and 2)~define a pNet action algebra that associates, as action parameter, an
+by the initial valuation $\val{0}{C}$ of $C$, 2)~define a pNet action algebra that associates, as action parameter, an
 additional Boolean value to each port, 3)~create pNet transitions that reflect the original transitions of
@@
 The encoding of the interaction model is based on its representation
-as a set of connectors. \noteSB{A legitimate question is whether we
-  actually need to do this, instead of listing explicitly the
-  individual interactions, then associating a synchronisation vector
-  to each one of them?  One of the factors is the encoding
-  pNets$\rightarrow$SAT: is it better to have more or fewer SVs if the
-  price is additional Boolean variables?  The other factor might be
-  the facility of maximal progress encoding\mdash TBC.  Traceability.
-  Anything else?  }Indeed, as illustrated by the Failure Monitor
-architecture in \fig{schema:ArchFailure:BIP}, each connector can
-define several allowed interactions, depending on its hierarchical
-structure and port and node syncrhon/trigger typings.  For instance,
-the connector {\NameTimer.\PortTick \trigsynch (\PortFail \trigsynch
-  \NameCtrl.\PortFail)} defines three interactions (observe that
-$\topinterval + \NameTimer.t = \topinterval$ and $\NameTimer.z \cap
-\topinterval = \NameTimer.z$):\noteSB{Move this to \secn{components}?}
+as a set of connectors. \noteSB{%
+%
+  A legitimate question is whether we actually need to do this,
+  instead of listing explicitly the individual interactions, then
+  associating a synchronisation vector to each one of them?  One of
+  the factors is the encoding pNets$\rightarrow$SAT: is it better to
+  have more or fewer SVs if the price is additional Boolean variables?
+  The other factor might be the facility of maximal progress
+  encoding\mdash TBC.  Traceability.  Anything else?
+%
+} Indeed, as illustrated by the Failure Monitor architecture in
+\fig{schema:ArchFailure:BIP}, each connector can define several
+allowed interactions, depending on its hierarchical structure and the
+use of syncrhons and trigger.  \noteSB{Move this to
+  \secn{components}?}For instance, the connector {\NameTimer.\PortTick
+  \trigsynch (\PortFail \trigsynch \NameCtrl.\PortFail)} is a
+two-level hierarchical connector.  In the second-level subconnector
+{\PortFail \trigsynch \NameCtrl.\PortFail}, the port {\PortFail} is a
+trigger, whereas {\NameCtrl.\PortFail} is a synchron.  Therefore, this
+subconnector allows two interactions: one with {\PortFail} alone and
+another one involving both ports.  Similarly, at the top level,
+{\NameTimer.\PortTick} is a trigger, whereas the second-level
+subconnector is a synchron.  Hence, this connector allows an
+interaction involving only one port {\NameTimer.\PortTick}\footnote{%
+%
+  Such interactions are called \emph{singleton interactions}.
+%
+} and any interaction involving both {\NameTimer.\PortTick} and
+\emph{some} interaction of the second-level subconnector.  Combining
+the two levels we can see that the entire connector defines the
+following three interactions (observe that $\topinterval +
+\NameTimer.t = \topinterval$ and $\NameTimer.z \cap \topinterval =
+\NameTimer.z$):
 %
@@
 
-In order to encode these using only one synchronisation vector, we use
+In order to encode these interactions using only one synchronisation vector, we use
 the additional Boolean values associated to each port by the encoding

### 2018-10-18 2018-Arch-pNets/arch-pNets.tex
Arch-pNet paper: further modifications in response to comments by Ludo: moved the explanation of how transitions marked by false are used to simulate non-participation of ports in an interaction (added a reference to Milner for the construction)

@@
 $\false$.
+%
+The loop transitions marked by $\false$ will be used in the encoding
+of connectors.  Each BIP connector can define several interactions,
+\ie ports involved in a connector need not necessarily always
+participate.  On the contrary, each action in a pNet synchronisation
+vector must participate in the synchronisation.  To address this
+difference, we use the classical~\cite{milner83-calculi} approach,
+whereby non-participation of a port in an interaction is simulated
+by an additional loop transition.
 
@@
 that, in our encoding, all three ports are present in the
-synchronisation vector.  Non-participation of a port corresponds to
-firing the loop transition marked by \false.  \Fig{enc:nopri} shows
+synchronisation vector.  \Fig{enc:nopri} shows
 the four synchronisation vectors SV0\ndash SV3 corresponding to the

### 2018-10-20 2018-Arch-pNets/arch-pNets.tex
Arch-pNet paper: Added an appendix with the summary of algebraic representations of connectors and encodings among them Added a figure with three representations of the four connectors from the Failure Monitor Added a simplified encoding (almost complete) -- to be replaced by the exact one, but committing for the record -- could be useful some other time.

@@
 \newcommand{\secn}[1]{Sect.~\ref{secn:#1}}
+\newcommand{\app}[1]{App.~\ref{secn:#1}}
 \newcommand{\rem}[1]{Note~\ref{rem:#1}}
@@
 \newcommand{\twosynch}{%
-  \ensuremath{\bullet\!\!\!-\!\!\!-\!\!\!-\!\!\!\bullet}}
+  \mbox{\ensuremath{\bullet\!\!\!-\!\!\!-\!\!\!-\!\!\!\bullet}}}
 \newcommand{\synchtrig}{%
-  \ensuremath{\bullet\!\!\!-\!\!\!-\!\!\!\blacktriangleleft}}
+  \mbox{\ensuremath{\bullet\!\!\!-\!\!\!-\!\!\!\blacktriangleleft}}}
 \newcommand{\trigsynch}{%
-  \ensuremath{\blacktriangleright\!\!\!-\!\!\!-\!\!\!\bullet}}
+  \mbox{\ensuremath{\blacktriangleright\!\!\!-\!\!\!-\!\!\!\bullet}}}
 \newcommand{\twotrig}{%
-  \ensuremath{\blacktriangleright\!\!\!-\!\!\!-\!\!\!\blacktriangleleft}}
+  \mbox{\ensuremath{\blacktriangleright\!\!\!-\!\!\!-\!\!\!\blacktriangleleft}}}
 
@@
 \newcommand{\expmix}{\wedge}
+
+\newcommand{\intsem}[1]{\ensuremath{\|{#1}\|}}
+\newcommand{\aisem}[1]{\ensuremath{|{#1}|}}
+
+\newtheorem*{syntax}{Syntax}
+\newtheorem*{semantics}{Semantics}
+
+\newcommand{\ai}{\ensuremath{\mathcal{AI}}}
+\newcommand{\ct}{\ensuremath{\mathcal{T}}}
+\newcommand{\cru}{\ensuremath{\mathcal{CR}}}
+\newcommand{\ac}{\ensuremath{\mathcal{AC}}}
 
@@
 %
-  where \noteSB{Can probably write directly $\overline{V_C := \val{0}{C}}$, in which case no need to intrudce $\mathit{init}$.}\hl{$\mathit{init} = \bigl(x := \val{0}{C}(x)\bigr)^{x \in V_C}$}.
+  where $\mathit{init} = \bigl(x := \val{0}{C}(x)\bigr)^{x \in V_C}$.
 \end{itemize}
-
-\noteSBin{Eric uses some kind of initialisation predicate in
-  Fig.~\ref{schema:ArchFailure:BIP}.  I do not quite understand how
-  this works, so I used a new initial state with explicit
-  initialisation.}
 
@@
 $\false$.
-%
+
 The loop transitions marked by $\false$ will be used in the encoding
@@
 have an associated Boolean value, nor the additional loop transitions.
-We will explicitate this optimisation once we have defined the
-encoding of the interaction model.
+\todoSB{Revise this if necessary}\hl{We will explicitate this optimisation once we have defined the
+encoding of the interaction model.}
 
@@
 Thus, the holes in the resulting pNet are indexed by the elements of
-partition \partition.  For the encoding of our running example, we
+the partition \partition.  For the encoding of our running example, we
 take $\partition = \bigl\{\{\PortFail, \PortResume\},\{\PortAsk,
@@
 {\NameTimer.\PortTick} is a trigger, whereas the second-level
-subconnector is a synchron.  Hence, this connector allows an
+subconnector is a synchron.  Hence, the overall connector allows the
 interaction involving only one port {\NameTimer.\PortTick}\footnote{%
@@
 \begin{align*}
-  &\bigl(\{\NameTimer.\PortTick\},
-  &&\true, 
-  &&\NameTimer.z := \NameTimer.z\bigr)
-  \\
-  &\bigl(\{\NameTimer.\PortTick, \PortFail\},
-  &&\true,
-  &&\NameTimer.z := \NameTimer.z\bigr)
-  \\
-  &\bigl(\{\NameTimer.\PortTick, \PortFail, \NameCtrl.\PortFail\},
-  &&\true,
-  &&\NameTimer.z := \NameTimer.z \cap (\NameCtrl.\mathit{zone} + \NameTimer.t)\bigr)
+  \bigl(\{\NameTimer.\PortTick\}&,
+  \true, 
+  \NameTimer.z := \NameTimer.z\bigr)
+  \,,\\
+  \bigl(\{\PortFail, \NameTimer.\PortTick\}&,
+  \true,
+  \NameTimer.z := \NameTimer.z\bigr)
+  \,,\\
+  \bigl(\{\NameCtrl.\PortFail, \PortFail, \NameTimer.\PortTick \}&,
+  \true,
+  \NameTimer.z := \NameTimer.z \cap (\NameCtrl.\mathit{zone} + \NameTimer.t)\bigr)
+  \,.\
 \end{align*}
@@
 as Boolean implications $\NameCtrl.\PortFail \Rightarrow \PortFail$
-and $\PortFail \Rightarrow \NameTimer.\PortTick$.  However, notice
+and $\PortFail \Rightarrow \NameTimer.\PortTick$.
+%
+The conjunction of these two implications can be used as a guard for
+the synchronisation vector encoding connector {\NameTimer.\PortTick
+  \trigsynch (\PortFail \trigsynch \NameCtrl.\PortFail)}.
+
+However, notice
 that, within the scope of this connector, {\NameTimer.\PortTick}
-participates in all the interactions, meaning that the latter
-implication is a tautology and can be discarded.  Thus, we obtain the
+participates in all the interactions.
+%
+Furthermore, {\NameTimer.\PortTick} is not involved in any other
+connector.  Therefore, the loop transition in \nopri[\NameTimer]
+labelled by $\PortTick(\false)$ can never be taken and, therefore can
+be removed from the encoding.  Furthermore, since only the transition
+labelled by $\PortTick(\true)$ is ever taken, 
+%
+the
+implication $\PortFail \Rightarrow \NameTimer.\PortTick$ is a tautology and can also be discarded.
+
+We obtain the
 synchronisation vector SV0 shown in \fig{enc:nopri}, where $b_0$ and
@@
 
+The general case encoding relies on the causal semantics of the
+algebra of BIP connectors \cite{BliSif10-causal-fmsd}.  Disregarding
+the variables and data transfer, the Algebra of Connectors $\ac(P)$
+\cite{BliSif07-acp-emsoft} provides a syntactic notation for the BIP
+connectors.  The causal semantics of the connectors, given in terms of
+the Algebra of Causal Interaction Trees $\ct(P)$, explicitates the
+causal dependencies discussed above, through an encoding mapping
+$\tau: \ac(P) \rightarrow \ct(P)$.  Another mapping $R: \ct(P)
+\rightarrow \cru(P)$ encodes causal interaction trees into systems of
+causal rules, which are Boolean implications similar to the ones in
+the example above.  We briefly summarise the key definitions and
+results in \app{algebras}.
+
+\begin{table}[t]
+  \caption{Algebraic representations of the connectors in \fig{schema:ArchFailure:BIP} (see \app{algebras})}
+  \label{tab:connectors}
+  \resizebox{\columnwidth}{!}{%
+  \begin{tabular}{@{}c|c|c@{}}
+    \hline {\bf Connector} & {\bf Causal Interaction Tree} & {\bf
+      System of Causal Rules}
+    \\\hline    
+%
+    \begin{tikzpicture}[shorten >=1pt,node distance=.7cm,>=stealth']
+
+      \node(caa) {}; % node distance=5cm [right of=start]
+      \node[node distance=1cm] (cb) [below of=caa]{\PortFail};
+      \node[node distance=1.8cm] (cc) [right of=cb]{\NameCtrl.\PortFail};
+      \node[node distance=1.6cm] (ca) [left of=cb]{\NameTimer.\PortTick};
+
+      \draw [style=-*, thick, black] ($(caa.south)+(0,.1cm)$) -- ++(right:.5cm) -| (cc.north);
+      \draw [style=-triangle 45 reversed, thick, black]  ($(caa.south)+(0,.1cm)$) -| (cb.north);
+      \draw [style=-*, thick, black] ($(caa.south)+(0,.5cm)$) -- ++(right:.2cm) -| ($(caa.south)+(+.9,0cm)$);
+      \draw [style=-triangle 45 reversed, thick, black]  ($(caa.south)+(0,.5cm)$) -| (ca.north);
+    \end{tikzpicture}
+%
+    &
+%
+    \begin{tikzpicture}[shorten >=1pt,node distance=.7cm,>=stealth'
+        ,initial text=
+        ,every state/.style={draw=black,thick}
+        ,group/.style = {draw=black,thin,rectangle, minimum width=2.5cm}
+        ,port/.style = {font=\small, minimum size=5mm}
+        ,legend/.style = {font=\bf}
+      ]
+
+      \node(tick){\color{red}\NameTimer.\PortTick};
+      \node[node distance=1cm](x) [right of=tick]{};
+      \node(fail) [below of=x] {\PortFail};
+      \node[node distance=1cm](y) [right of=fail]{};      
+      \node(ctrlfail) [below of=y] {\NameCtrl.\PortFail};
+
+      \draw[style=->] (tick) -> (fail);
+      \draw[style=->] (fail) -> (ctrlfail);
+    \end{tikzpicture}
+%
+    &
+%
+    $
+    \begin{aligned}[b]
+      \NameCtrl.\PortFail &\Rightarrow
+      \PortFail {\color{red}{}\land \NameTimer.\PortTick}
+      \\
+      {\color{red}\PortFail} &{\color{red}{}\Rightarrow \NameTimer.\PortTick}
+      \\
+      {\color{red}\NameTimer.\PortTick} &{\color{red}{}\Rightarrow \true}
+      \\
+      {\color{red}\true} &{\color{red}{}\Rightarrow \NameTimer.\PortTick}
+
+    \end{aligned}
+    $
+%
+    \\\hline
+%
+    \begin{tikzpicture}[shorten >=1pt,node distance=.7cm,>=stealth']
+
+      \node[](baa) {}; % node distance=1.8cm [right of=start]
+      \node[node distance=1cm] (bb) [below of=baa]{\NameTimer.\PortCancel};
+      \node[node distance=1.8cm] (bc) [right of=bb]{\NameCtrl.\PortResume};
+      \node[node distance=1.6cm] (ba) [left of=bb]{\PortResume};
+
+      \draw [style=-*, thick, black] ($(baa.south)+(0,.1cm)$) -- ++(right:.5cm) -| (bc.north);
+      \draw [style=-*, thick, black]  ($(baa.south)+(0,.1cm)$) -| (bb.north);
+      \draw [style=-*, thick, black] ($(baa.south)+(0,.5cm)$) -- ++(right:.2cm) -| ($(baa.south)+(+.9,0cm)$);
+      \draw [style=-triangle 45 reversed, thick, black]  ($(baa.south)+(0,.5cm)$) -| (ba.north);
+    \end{tikzpicture}
+%
+    &
+%
+    \begin{tikzpicture}[shorten >=1pt,node distance=.7cm,>=stealth'
+        ,initial text=
+        ,every state/.style={draw=black,thick}
+        ,group/.style = {draw=black,thin,rectangle, minimum width=2.5cm}
+        ,port/.style = {font=\small, minimum size=5mm}
+        ,legend/.style = {font=\bf}
+      ]
+
+      \node(res){\color{red}\PortResume};
+      \node[node distance=1cm](rest) [below of=res] {\NameTimer.\PortCancel\ \NameCtrl.\PortResume};
+      \draw[style=->] (res) -> (rest);
+    \end{tikzpicture}
+%
+    &
+%
+    $
+    \begin{aligned}[b]
+      \NameCtrl.\PortResume &\Rightarrow
+      {\color{red}\PortResume \land{}} \NameTimer.\PortCancel
+      \\
+      \NameTimer.\PortCancel &\Rightarrow 
+      {\color{red}\PortResume \land{}} \NameCtrl.\PortResume
+      \\
+      {\color{red}\PortResume} &{\color{red}{}\Rightarrow \true}
+      \\
+      {\color{red}\true} &{\color{red}{}\Rightarrow \PortResume}
+    \end{aligned}
+    $
+%
+    \\\hline
+%
+    \begin{tikzpicture}[shorten >=1pt,node distance=.7cm,>=stealth']
+
+      \node (start) {};
+      \node(h4)[left of=start]{}; %, node distance=1.5cm
+
+      \node[node distance=1cm] (ab) [below of=start] {\NameTimer.\PortTO};
+      \node[node distance=2.1cm] (ac) [right of=ab]{\NameCtrl.\PortTO};
+      \node[node distance=1.5cm] (aa) [left of=ab]{\PortAsk};
+
+      \draw [style=-*, thick, black] ($(h4.south)+(0,.1cm)$) -- ++(right:.5cm) -| (ac.north);
+      \draw [style=-*, thick, black]  ($(h4.south)+(0,.1cm)$) -| (ab.north);
+      \draw [style=-*, thick, black]  ($(h4.south)+(0,.1cm)$) -| (aa.north);
+    \end{tikzpicture}
+%
+    &
+%
+    \begin{tikzpicture}[shorten >=1pt,node distance=.7cm,>=stealth']
+      \node (start) {\color{red}\PortAsk\ \NameTimer.\PortTO\ \NameCtrl.\PortTO};
+      \node()[below of=start]{};
+    \end{tikzpicture}
+%
+    &
+%
+    $
+    \begin{array}[b]{c@{}}
+      {\color{red}
+        \begin{aligned}
+          \NameCtrl.\PortTO &\Rightarrow
+          \PortAsk \land \NameTimer.\PortTO
+          \\
+          \NameTimer.\PortTO &\Rightarrow 
+          \PortAsk \land \NameCtrl.\PortTO
+        \end{aligned}}
+      \\[11pt]
+      {\color{red}
+        \begin{aligned}
+          \PortAsk &\Rightarrow
+          \NameTimer.\PortTO \land \NameCtrl.\PortTO
+          \\
+          \true &\Rightarrow
+          \PortAsk \land \NameTimer.\PortTO
+          \land \NameCtrl.\PortTO
+        \end{aligned}
+
+      }
+    \end{array}
+    $
+    %
+    \\\hline
+%
+    \begin{tikzpicture}[shorten >=1pt,node distance=.7cm,>=stealth']
+
+      \node (start) {};
+      \node(h4)[left of=start]{}; %, node distance=1.5cm
+
+      \node[node distance=1cm] (ab) [below of=start] {\NameCtrl.\PortReset};
+      \node[node distance=1.5cm] (aa) [left of=ab]{\PortReset};
+
+      \draw [style=-*, thick, black]  ($(h4.south)+(0,.1cm)$) -| (ab.north);
+      \draw [style=-*, thick, black]  ($(h4.south)+(0,.1cm)$) -| (aa.north);
+    \end{tikzpicture}
+%
+    &
+%
+    \begin{tikzpicture}[shorten >=1pt,node distance=.7cm,>=stealth']
+      \node (start) {\color{red}\PortReset\ \NameCtrl.\PortReset};
+      \node()[below of=start]{};
+    \end{tikzpicture}
+%
+    &
+%
+    {\color{red}$
+    \begin{aligned}[b]
+      \NameCtrl.\PortReset &\Rightarrow \PortReset
+      \\
+      \PortReset &\Rightarrow \NameCtrl.\PortReset
+      \\
+      \true &\Rightarrow
+      \PortReset \land \NameCtrl.\PortReset
+    \end{aligned}
+    $}
+%
+    \\\hline
+  \end{tabular}}
+\end{table}
+
+First, consider a flat connector with $n$ trigger ports $p_1,\dots,
+p_n$ (with $n > 0$) and $m$ synchron ports $q_1,\dots, q_m$
+(\fig{connector}).  Similarly to the example above, for any of the
+ports $q_1,\dots, q_m$ to participate in an interaction defined by
+this connector, at least one of the ports $p_1,\dots, p_n$ must
+participate.  This causal dependency can be represented by the Boolean
+formula $q_1 \lor \dots \lor q_m \Rightarrow p_1 \lor \dots \lor p_n$.
+If there are no synchrons, \ie $m = 0$, this formula simplifies to
+$p_1 \lor \dots \lor p_n$.  However, if there are no triggers, \ie $n
+= 0$, the connector semantics is that \emph{all} synchron ports must
+participate for an interaction to take place, represented by the
+Boolean formula $(q_1 = q_2) \land \dots \land (q_1 = q_m)$.
+
+We now generalise this principle to hierarchical connectors, building
+the formula bottom-up.  In a flat connector above, we have implicitly
+associated a Boolean variable to each port.  In a hierarchical
+connector, we associate a fresh Boolean variable to each node.
+Similarly to the above example, consider a connector with $n > 0$
+trigger sub-connectors and $m$ synchron sub-connectors.  We associate
+to this connector a fresh Boolean variable $x$.  Assume that Boolean
+variables associated to trigger sub-connectors are $x_1,\dots,x_n$,
+whereas those associated to synchron sub-connectors are
+$y_1,\dots,y_m$.  The causal dependencies among the interactions
+defined by the sub-connectors can be encoded by the formula
+%
+\begin{equation}
+  \label{eq:trig:encoding}
+  (y_1 \lor \dots \lor y_m \Rightarrow x) \land (x = x_1 \lor \dots
+  \lor x_n).
+\end{equation}
+%
+If there are no trigger sub-connectors, \ie $n = 0$, we use the
+formula
+%
+\begin{equation}
+  \label{eq:synch:encoding}
+  x = \bigl((y_1 = y_2) \land \dots \land (y_1 = y_m)\bigr)
+\end{equation}
+%
+($x$ is equal to $\true$ if all $x_1, \dots, x_m$ are equal, it is
+equal to $\false$ otherwise).
+
+Notice that, in the flat connector example above, the formula was
+essentially the same, with $p_i$ instead of $x_i$ and $q_i$ instead of
+$y_i$, and without the additional variable $x$.  Indeed, $x$ is used
+to encode the causal dependencies between this connector and, if
+necessary, those in higher levels of the hierarchy.  The Boolean
+encoding of the causal dependencies among the ports of the entire
+connector is obtained by taking the conjunction of formulas obtained
+for each sub-connector.
+
+Consider again the connector {\NameTimer.\PortTick \trigsynch
+  (\PortFail \trigsynch \NameCtrl.\PortFail)}.  Associating the
+varaibles $b_0$, $b_1$ and $b_2$ to ports {\PortFail},
+{\NameCtrl.\PortFail} and {\NameTimer.\PortTick}, respectively, and
+variables $y_1$ and $y_2$ to the top- ({\NameTimer.\PortTick
+  \trigsynch $\cdot$}) and second-level (\PortFail \trigsynch \NameCtrl.\PortFail) connectors in the hierarchy,
+we obtain the following formula
+%
+\begin{equation}
+  \label{eq:tff:example}
+  (b_1 \Rightarrow y_2) \land (y_2 = b_0) \land (y_2 \Rightarrow y_1)
+  \land (y_1 = b_2)
+  \,.
+\end{equation}
+%
+Observe now that the top-level connector, by its very nature, does not
+have any higher level connectors and therefore we can eliminate the
+corresponding Boolean variable.  This simplifies \eq{tff:example}, to
+%
+\begin{equation}
+  \label{eq:tff:example:1}
+  (b_1 \Rightarrow y_2) \land (y_2 = b_0) \land (y_2 \Rightarrow b_2)
+  \,.
+\end{equation}
+%
+In the general case, this corresponds to replacing, \emph{for
+  top-level connectors}, equations \eq{trig:encoding} and
+\eq{synch:encoding}, respectively, by
+%
+\begin{gather}
+  \label{eq:trig:encoding:1}
+  y_1 \lor \dots \lor y_m \Rightarrow x_1 \lor \dots
+  \lor x_n
+  \\
+  \intertext{and}
+  \label{eq:synch:encoding:1}
+  (y_1 = y_2) \land \dots \land (y_1 = y_m)
+  \,.
+\end{gather}
+%
+Furthermore, in the context of one connector (or synchronisation
+vector), some interaction must be fired.  Thus, \emph{for top-level
+  connectors}, \eq{synch:encoding:1} can be further simplified to 
+%
+\begin{equation}
+  \label{eq:synch:encoding:2}
+  y_1 \land \dots \land y_m
+  \,.
+\end{equation}
+
 %****************************************************************
@@
 
+%****************************************************************
+%****************************************************************
+
 \section{Proofs}
+\label{secn:proofs}
 
@@
 
+%*********************************************************************
+%*********************************************************************
+
 \section{pNets additional definitions}
+\label{secn:pNets:additional}
+
 \begin{definition}[Sorts, Holes, Leaves of pNets]
@@
 
+%*********************************************************************
+%*********************************************************************
+
+\section{Algebraic representations of the interaction model}
+\label{secn:algebras}
+
+In this section condensed from
+\cite[Section~4]{BarBliu15-offer-scico}, we briefly recall the syntax
+and semantics of the algebras used to represent BIP interaction models
+\emph{disregarding variables and data transfer}.  All the algebras are
+parameterised by a set $P$ of all the ports in a given system.  The
+semantics of the Algebra of Interactions $\ai(P)$ is given in terms of
+sets of interactions by a function $\intsem{\cdot}: \ai(P) \rightarrow
+2^{2^P}$.  The corresponding equivalence relation on $\ai(P)$ is
+defined as follows: two terms $x,y \in \ai(P)$ are {\em equivalent} $x
+\simeq y$ iff $\intsem{x} = \intsem{y}$.  For any other algebra
+$\cA(P)$ among those appearing in this section, we define its
+semantics by the function $\aisem{\cdot}: \cA(P) \rightarrow \ai(P)$.
+A function $\intsem{\cdot}: \cA(P) \rightarrow 2^{2^P}$ is obtained by
+composing $\aisem{\cdot}: \cA(P) \rightarrow \ai(P)$ and
+$\intsem{\cdot}: \ai(P) \rightarrow 2^{2^P}$.  The axiomatisation of
+$\ai(P)$ given in \cite{BliSif07-acp-emsoft} is sound and complete
+with respect to $\simeq$.  Hence, for other algebras, the equivalences
+induced by $\intsem{\cdot}$ and $\aisem{\cdot}$ coincide.
+
+Below, we assume that a set of ports $P$ is given, such that $0,1\not\in
+P$.
+
+For any set $X$ of propositional variables, we denote by $\sB[X]$ the
+corresponding Boolean algebra generated by $X$.  For presentation
+clarity, we will often omit the conjunction operator and write $a \lor
+bc$ instead of $a \lor (b \land c)$.
+
+% *********************************************************************
+
+\subsection{Algebra of Interactions}
+\label{secn:ai}
+
+The Algebra of Interactions is used to define the interaction semantics of other algebras. The elements of this algebra can be bijectively mapped to interaction models, \ie subsets of $2^P$.
+
+\begin{syntax}
+The syntax of the {\em Algebra of Interactions}, $\ai(P)$, is defined by
+the following grammar
+%
+\begin{equation} \label{eq:apsynt}
+  \begin{array}{rc*{4}{l@{\ |\ }}l}
+    x & ::= & 0 & 1 & p \in P & x\cdot x & x + x \,,\\
+  \end{array}
+\end{equation}
+%
+where `$+$' and `$\cdot$' are binary operators, respectively called
+{\em union} and {\em synchronisation}.  Synchronisation binds stronger
+than union.
+\end{syntax}
+%
+As follows from the interaction semantics given below, the additive
+identity element $0$ represents blocking, since it does not authorise
+any interaction.  The multiplicative identity element $1$ corresponds
+to the empty interaction, which represents idling (see the discussion
+in \cite{BarBliu15-offer-scico}).
+
+\begin{semantics}
+The semantics of $\ai(P)$ is given by the function $\|\cdot\| : \ai(P)
+\rightarrow 2^{2^P}$, defined by
+%
+\begin{equation} \label{eq:apsem}
+  \renewcommand{\arraystretch}{1.5}
+  \begin{array}{lcl}
+    \lefteqn{\|0\|\ =\ \emptyset,\quad \|1\|\ =\ \{\emptyset\},\quad
+      \|p\|\ =\ \Big\{\{p\}\Big\},}\\
+    \|x_1 + x_2\| &=& \|x_1\| \cup \|x_2\|,\\
+    \|x_1 \cdot x_2\| &=& 
+    \Big\{a_1 \cup a_2\,\Big|\, a_1\in \|x_1\|, a_2\in \|x_2\| \Big\},
+  \end{array}
+\end{equation}
+for $p\in P$, $x_1,x_2\in\ai(P)$.  Terms of $\ai(P)$ represent sets of
+interactions between the ports $P$.
+\end{semantics}
+
+A sound and complete axiomatisation of $\ai(P)$ with respect to the
+semantic equivalence is provided in \cite{BliSif07-acp-emsoft}.  In a
+nutshell, $(\ai(P), +, \cdot, 0, 1)$ is a commutative semiring,
+idempotent in both $+$ and $\cdot$.
+
+% *********************************************************************
+
+\subsection{Algebra of Connectors}
+\label{secn:ac}
+
+The Algebra of Connectors provides an algebraic formalisation for
+structuring the interaction models.  It underlies the graphical
+notation (\eg \fig{connectors}) and the syntax for connectors used in the BIP language.
+
+\begin{syntax}
+The syntax of the {\em Algebra of Connectors}, $\ac(P)$, is defined by the
+following grammar
+%
+\begin{equation} \label{eq:acsynt}
+  \renewcommand{\arraystretch}{1.5}
+  \begin{array}{lcll}
+    s & ::= & [0]\ |\ [1]\ |\ [p]\ |\ [x] \:\:\:\:\:\:\:\:\:(synchrons)\\
+    t & ::= & [0]'\ |\ [1]'\ |\ [p]'\ |\ [x]'  \:\:\:\:\:\:   (triggers)\\
+    x & ::= & s\ |\ t\ |\ x\cdot x\ |\ x + x\,, 
+  \end{array}
+\end{equation}
+for $p\in P$, and where `$+$' is a binary operator called {\em union},
+`$\cdot$' is a binary operator called {\em fusion}, and brackets
+`$[\cdot]$' and `$[\cdot]'$' are unary {\em typing} operators.  Fusion
+binds stronger than union.
+
+Union has the same meaning as union in $\ai(P)$. Fusion is a
+generalisation of the synchronisation in $\ai(P)$.  Typing is used to
+form typed connectors: `$[\cdot]$' defines {\em synchrons} (need
+synchronisation with other ports in order to interact) and
+`$[\cdot]'$' defines {\em triggers} (can initiate an interaction).
+\end{syntax}
+
+In order to simplify notation, we will omit brackets on 0, 1, and
+ports $p \in P$, as well as `$\cdot$' for the fusion operation.
+
+\begin{definition}
+ In a system with a set of ports $P$, connectors are elements of $\ac(P)$.
+\end{definition}
+
+The operations of the Algebra of Connectors satisfy the following
+axioms.
+\begin{itemize}
+\item Union `$+$' is associative, commutative, idempotent and has the identity element 0.
+\item Fusion `$\cdot$' is associative, commutative and has the identity element 1.
+It is idempotent on monomial connectors, \ie[,] for any $x \in \ac(P)$, not involving the union operation, we have $x\cdot x = x$.
+\item Typing `$[\cdot]^*$' satisfies the following axioms, for $x,y,z
+  \in \ac(P)$ and $[\cdot]^\alpha,[\cdot]^\beta \in \bigl\{[\cdot]', [\cdot]\bigr\}$ arbitrary typings (trigger or synchron):
+  \begin{enumerate}
+  \item $[0] = [0]'$,
+  \item $[[x]^\alpha]^\beta = [x]^\beta$,
+  \item $[x + y]^\alpha = [x]^\alpha + [y]^\alpha$,
+  \item $[x]'[y]' = [x]'[y] + [x][y]'$.
+  \end{enumerate}
+\end{itemize}
+Complete axiomatisation of $\ac(P)$ with respect to the semantic
+equivalence is provided in \cite{BliSif08-acp-tc}.
+
+\begin{semantics}
+The semantics of $\ac(P)$ is given by the function $|\cdot| : \ac(P)
+\rightarrow \ai(P)$ (we use the $\sum$ and $\prod$ notation for,
+respectively, the union and fusion of multiple terms of $\ac(P)$):
+%
+\begin{align}
+  \label{eq:acap}
+  |[p]| & = p\,,
+  & |x_1 + x_2| & = |x_1| + |x_2|\,,
+  & \left|\prod_{i=1}^n [x_i]\,\right| & = \prod_{i=1}^n |x_k|\,,
+  \\
+  \label{eq:acaptrig}
+  && \hspace{-2cm}\left|\prod_{i=1}^n [x_i]' \prod_{j=1}^m [y_j]\,\right| = 
+  \sum_{i=1}^n |x_i| & \lefteqn{\left(
+  \prod_{k\not=i}\Big(1 + |x_k|\Big)\ \prod_{j=1}^m \Big(1 + |y_j|\Big)\right)}\,
+\end{align}
+%
+for $n > 0$, $m \geq 0$, $x_1,\dots,x_n,y_1,\dots,y_m \in \ac(P)$ and
+$p\in P\cup \{0,1\}$.
+\end{semantics}
+
+\fig{connectors} shows four basic examples of the graphical
+representation of connectors.  Triggers are denoted by triangles,
+whereas synchrons are denoted by bullets.  The interaction semantics
+of the four connectors is given in the sub-figure captions.
+
+\begin{figure}
+  \centering
+  \begin{subfigure}[b]{0.18\textwidth}
+    %% \rule{\textwidth}{0.5pt}
+    \centering
+    \input{figures/rdv.pspdftex}
+    \caption{\centering Rendezvous~$pqr$
+      $\intsem{pqr} = \{pqr\}$}
+    \label{fig:connectors:rdv}
+  \end{subfigure}%
+  \hfill %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+  %(or a blank line to force the subfigure onto a new line)
+  \begin{subfigure}[b]{0.24\textwidth}
+    %% \rule{\textwidth}{0.5pt}
+    \centering
+    \input{figures/broadcast.pspdftex}
+    \caption{\centering Broadcast~$p'qr$
+      $\intsem{p'qr} = \{p, pq, pr, pqr\}$}
+    \label{fig:connectors:bdc}
+  \end{subfigure}%
+  \hfill %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+  %(or a blank line to force the subfigure onto a new line)
+  \begin{subfigure}[b]{0.24\textwidth}
+    %% \rule{\textwidth}{0.5pt}
+    \centering
+    \input{figures/atomic-bdc.pspdftex}
+    \caption{\centering Atomic broadcast~$p'[qr]$
+      $\intsem{p'[qr]} = \{p, pqr\}$}
+    \label{fig:connectors:atomic}
+  \end{subfigure}%
+  \hfill %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+  %(or a blank line to force the subfigure onto a new line)
+  \begin{subfigure}[b]{0.23\textwidth}
+    %% \rule{\textwidth}{0.5pt}
+    \centering
+    \input{figures/causal-chain.pspdftex}
+    \caption{\centering Causal chain~$p'[q'r]$
+      $\intsem{p'[q'r]} = \{p, pq, pqr\}$}
+    \label{fig:connectors:causal}
+  \end{subfigure}%
+  \caption{Basic connector examples}
+  \label{fig:connectors}
+\end{figure}
+
+The semantic equivalence $\simeq$ is not a congruence for $\ac(P)$.
+We denote by $\cong$ the largest congruence relation contained in
+$\simeq$.
+
+\begin{property}[\cite{BliSif08-acp-tc}]
+  \label{prop:cong}
+  For any $x, y \in \ac(P)$, we have $[x]'[y]' \cong \bigl[[x]'[y]'\bigr]'$.
+\end{property}
+
+%*********************************************************************
+
+\subsection{Algebra of Causal Interaction Trees}
+\label{secn:trees}
+
+The Algebra of Causal Interaction Trees serves as a pivot for
+transformations between all other algebraic representations.  It makes
+explicit the causal dependencies between ports contributing to the
+interactions defined by a connector.
+
+\begin{syntax}
+The syntax of the \emph{Algebra of Causal Interaction Trees}, $\ct(P)$, is
+given by
+\begin{equation} \label{eq:ctsyn}
+  t ::= a \,|\, a \rightarrow t \,|\, t\oplus t\,,
+\end{equation}
+where $a \in \ai(P)$ is an interaction, \ie $0$, $1$ or a
+synchronisation of ports (without the use of the union operator), and
+`$\rightarrow$' and `$\oplus$' are respectively the {\em causality}
+and the {\em parallel composition} operators.  Causality binds
+stronger than parallel composition.  Notice that a causal interaction
+tree can have several roots.
+\end{syntax}
+
+``Atomic'' strongly synchronised interactions in the nodes of a causal
+interaction tree are the building blocks for the interactions provided
+by the connector.  The causality operator defines a dependency between
+two interactions: $a \rightarrow b$ means that for $b$ to
+participate in the overall interaction, $a$ must also participate.
+The parallel composition allows one to combine interactions without
+introducing dependencies: any combination of $a$
+and $b$ can participate in $a \oplus b$.
+
+The causality operator is right- (but not left-) associative: for
+interactions $a_1,\dots,a_n$, we have $a_1 \rightarrow (a_2
+\rightarrow (\dots \rightarrow a_n)\dots)) = a_1 \rightarrow a_2
+\rightarrow \dots \rightarrow a_n$.  We call this construction a {\em
+  causal chain}.
+
+\begin{semantics}
+The semantics of $\ct(P)$ is given by the function $|\cdot|: \ct(P)
+\rightarrow \ai(P)$
+\begin{align}
+  \label{eq:ctsem}
+  |a| & = a\,,
+  & |a \rightarrow t| & = a\Big(1 + |t|\Big)\,,
+  & |t_1 \oplus t_2| & = |t_1| + |t_2| + |t_1|\,|t_2|\,,
+\end{align}
+where $a\in 2^P \cup \{0,1\}$ is an interaction and $t, t_1, t_2 \in \ct(P)$.
+\end{semantics}
+
+A sound axiomatisation of $\ct(P)$ is provided in
+\cite{BliSif10-causal-fmsd}.
+
+% *********************************************************************
+
+\subsection{Systems of Causal Rules}
+\label{secn:rules}
+
+Systems of causal rules represent an intermediate structure between
+causal interaction trees and arbitrary Boolean formulas.  They
+directly encode the causality information explicit in the causal
+interaction trees, by transforming causality relations into dual Horn
+clauses. %%  Apart from supporting connector synthesis, they provide a
+%% convenient way for expressing properties to be enforced by the glue
+%% operators (see \secn{example} for some examples).  Causal rules
+%% have also served as basis for the macro-notation used to specify
+%% the glue in Dy-BIP\mdash a dynamic flavour of BIP \cite{dybip}.
+
+\begin{definition}
+  A {\em causal rule} is a Boolean formula in $\sB[P]$ of the form $E
+  \Rightarrow C$.  The \emph{effect} $E$ is either the constant
+  $\true$ or a port variable $p \in P$.  The \emph{cause} $C$ is
+  either a constant, $\true$ or $\false$, or a disjunction of
+  interactions, \ie $\bigvee_{i=1}^n a_i$ where, for all $i\in [1,n]$,
+  $a_i$ are conjunctions of positive port variables.
+\end{definition}
+
+\begin{note} \label{rem:absorption}
+  Notice that $a_1 \lor a_1\,a_2 = a_1$, and therefore causal rules
+  can be simplified by replacing $p \Rightarrow a_1 \lor a_1\,a_2$
+  with $p \Rightarrow a_1)$.  We assume that all the causal rules are
+  simplified by this absorption rule.
+\end{note}
+
+\begin{definition}
+  A \emph{system of causal rules} is a set $R = \{p \Rightarrow
+  x_p\}_{p\in P\cup \{\true\}}$.  An interaction $a \in 2^P$ satisfies
+  the system $R$ (denoted $a \models R$), iff the characteristic
+  valuation of $a$ on $P$ satisfies the formula $\bigwedge_{p\in P\cup
+    \{\true\}} (p \Rightarrow x_p)$.  We denote by
+  $|R|\ \bydef{=}\ \sum_{a \models R} a$ the union (in terms of the
+  Algebra of Interactions) of the interactions satisfying $R$.  Thus
+  we have $|\cdot| : \cru(P) \rightarrow \ai(P)$, where $\cru(P)$ is
+  the set of all systems of causal rules over the set of port
+  variables $P$.
+\end{definition}
+
+%*********************************************************************
+
+\subsection{Transformations between algebraic representations of interaction models}
+\label{secn:transformations}
+
+Transformations $\ac(P)
+\overset{\tau}{\underset{\sigma}{\rightleftarrows}} \ct(P)$, $\ct(P)
+\overset{R}{\rightleftarrows} \cru(P)$ and $\cru(P) \rightleftarrows
+\sB[P]$ were defined in \cite{BliSif10-causal-fmsd} and have been
+shown to respect $\simeq$.  Below, we recall only the transformations
+that are used in this paper.
+
+We define the function $\tau : \ac(P) \rightarrow \ct(P)$, associating
+a causal interaction tree with a connector.  By \prop{cong}, and the
+associativity of both fusion in $\ac(P)$ and parallel composition in
+$\ct(P)$, the following equations are sufficient to define $\tau$:
+%
+\begin{align}
+  \label{eq:contree:p}
+  \tau(p) &= p
+  \,,\\
+  \label{eq:contree:trigsynch}
+  \tau\left(
+  [x]'\prod_{i=1}^n [y_i]
+  \right) &=
+  \tau(x) \rightarrow \bigoplus_{i=1}^n \tau(y_i)
+  \,,\\
+  \label{eq:contree:trig}
+  \tau\bigl([x_1]'[x_2]'\bigr) &= \tau(x_1) \oplus \tau(x_2)
+  \,,\\
+  \label{eq:contree:sync}  
+  \tau\bigl([y_1][y_2]\bigr) &=
+  \bigoplus_{i = 1}^{m_1}\bigoplus_{j = 1}^{m_2} a_i^1 a_j^2
+  \rightarrow (t_i^1 \oplus t_j^2)
+  \,,
+\end{align}
+%
+where $x, x_1, x_2, y_1,\dots, y_n \in \ac(P)$, $p \in P \cup \{0,1\}$
+and, in \eq{contree:sync}, we assume $\tau(y_k) = \bigoplus_{i =
+  1}^{m_k} a_i^k \rightarrow t_i^k$, for $k = 1,2$.
+
+%% $\sigma : \ct(P) \rightarrow \ac(P)$ is defined recursively by putting
+%% %
+%% \begin{align}
+%%   \label{eq:treecon}
+%%   \sigma(a) & = [a]\,,
+%%   & \sigma(a \rightarrow t) & = [a]'\,[\sigma(t)]\,,
+%%   & \sigma(t_1 \oplus t_2)  & = [\sigma(t_1)]'\,[\sigma(t_2)]'\,.
+%% \end{align}
+
+We define $R: \ct(P) \rightarrow \cru(P)$ by putting
+%
+\begin{equation} 
+  \label{eq:trees2rules}
+  R(t)\ =\ \{p \Rightarrow c_p(t)\}_{p\in P\cup\{\true\}}\,,
+\end{equation}
+where the function $c_p : \ct(P) \rightarrow \sB[P]$ is defined recursively
+as follows.  For $a\in 2^P$ (with $p\not\in a$) and $t,t_1,t_2 \in \ct(P)$,
+we put
+%
+\begin{align*}
+  c_p(0) & = \false\,, 
+  & c_{\true}(0) & = \false\,,\\
+  c_p(p \rightarrow t) & = \true\,,
+  & c_{\true}(1 \rightarrow t) & = \true\,,\\
+  c_p(pa \rightarrow t) & = a\,,\\
+  c_p(a \rightarrow t) & = a \land c_p(t)\,,
+  & c_{\true}(a \rightarrow t) & = a\,,\\
+  c_p(t_1 \oplus t_2) & = c_p(t_1) \lor c_p(t_2)\,, 
+  & c_{\true}(t_1 \oplus t_2) & = c_{\true}(t_1) \lor c_{\true}(t_2)\,.
+\end{align*}
+
+Observe that this transformation associates to each port $p \in P$ a
+causal rule $p \Rightarrow C$, where $C$ is the disjunction of all
+prefixes leading from roots of $t$ to some node containing $p$,
+including the ports of this node other than $p$.
+
 \end{document}

### 2018-10-20 2018-Arch-pNets/arch-pNets.tex
Arch-pNets paper: Finished a first draft of the encoding without priorities

@@
 \usepackage{stmaryrd} % double brackets (\llbracket, \rrbracket)
+\usepackage{units}    % for nicefrac: x/y
 
@@
   \tupleDeli\docsvlist{#2}\tupleDelii% Process list
+}
+
+\newcommand{\Tuple}[2][\ensuremath{,\allowbreak}]{%
+  \setTupleDelims[\Big(]{\Big)}%
+  \tuple[#1]{#2}%
 }
@@
 
-\begin{definition}[pNets]\label{def-pnets}
+\begin{definition}[pNets]\label{defn:pnets}
 A pNet is a hierarchical structure where leaves are pLTSs and holes\footnote{Typing can 
@@
 \begin{definition}[Open transitions]
-	\label{def:OpenTransitions}
+	\label{defn:OpenTransitions}
 	An \emph{open transition} over a
@@
 \begin{definition}[Open automaton]
-	\label{def:open-automaton}
+	\label{defn:open-automaton}
 	An \emph{open automaton} is a structure\\ $A =
@@
 \begin{definition}[Operational semantics of open pNets]
-	\label{def:operationalSemantics}
+	\label{defn:operationalSemantics}
 	The semantics of a pNet $p$ is an open automaton $A = 
@@
 the example above.  We briefly summarise the key definitions and
-results in \app{algebras}.
+results in \app{algebras}.  The $\ac(P)$, $\ct(P)$ and $\cru(P)$
+representations of the connectors in \fig{schema:ArchFailure:BIP} are
+shown in \tab{connectors}.
 
@@
 
-First, consider a flat connector with $n$ trigger ports $p_1,\dots,
-p_n$ (with $n > 0$) and $m$ synchron ports $q_1,\dots, q_m$
-(\fig{connector}).  Similarly to the example above, for any of the
-ports $q_1,\dots, q_m$ to participate in an interaction defined by
-this connector, at least one of the ports $p_1,\dots, p_n$ must
-participate.  This causal dependency can be represented by the Boolean
-formula $q_1 \lor \dots \lor q_m \Rightarrow p_1 \lor \dots \lor p_n$.
-If there are no synchrons, \ie $m = 0$, this formula simplifies to
-$p_1 \lor \dots \lor p_n$.  However, if there are no triggers, \ie $n
-= 0$, the connector semantics is that \emph{all} synchron ports must
-participate for an interaction to take place, represented by the
-Boolean formula $(q_1 = q_2) \land \dots \land (q_1 = q_m)$.
-
-We now generalise this principle to hierarchical connectors, building
-the formula bottom-up.  In a flat connector above, we have implicitly
-associated a Boolean variable to each port.  In a hierarchical
-connector, we associate a fresh Boolean variable to each node.
-Similarly to the above example, consider a connector with $n > 0$
-trigger sub-connectors and $m$ synchron sub-connectors.  We associate
-to this connector a fresh Boolean variable $x$.  Assume that Boolean
-variables associated to trigger sub-connectors are $x_1,\dots,x_n$,
-whereas those associated to synchron sub-connectors are
-$y_1,\dots,y_m$.  The causal dependencies among the interactions
-defined by the sub-connectors can be encoded by the formula
+Below, we assume that, as in \fig{schema:ArchFailure:BIP}, the
+interaction model is defined by a set of connectors, annotated with
+Boolean guards and with update assignments.  In particular, we assume
+that the guards and update assignments are well-defined for any
+interaction allowed by the connector.  For example, the choice
+$\NameCtrl.\PortFail\ ?\ \NameCtrl.\mathit{zone} : \topinterval$ in
+the update assignement
+\[
+\NameTimer.\mathit{z} := \NameTimer.\mathit{z}
+\cap \Big(
+\bigl(
+\NameCtrl.\PortFail\ ?\ \NameCtrl.\mathit{zone} : \topinterval
+\bigr)
++ \NameTimer.\mathit{t} \Big)
+\]
+associated to the connector {\NameTimer.\PortTick \trigsynch
+  (\PortFail \trigsynch \NameCtrl.\PortFail)} in
+\fig{schema:ArchFailure:BIP} ensures that the assignment is
+well-defined independently of whether {\NameCtrl.\PortFail}
+participates or not.  Let us denote by $\gamma \subset \ac(P_A)
+\times \guards{V_A} \times \assigns{V_A}$ the set of connectors in the
+architecture $A$ and by $P_x$ the set of ports involved in the
+connector $x \in \gamma$.  Then, we have
+\begin{align*}
+  \gamma &=
+  \setdef{(x, g, u)}{x \in \ac(P_x), g \in \guards{V_x}, u \in
+    \assigns{V_x}}
+  \\
+  &\simeq \setdef{(a,g,u)}{(x,g,u) \in \gamma, a \in \intsem{x}}
+  = \Gamma
+  \,.
+\end{align*}
+
+We first define the encoding of $\Gamma$ as $\nopri[\Gamma] \bydef{=}
+\setdef{\nopri[x,g,u]}{(x,g,u) \in \gamma}$, where $\nopri[x,g,u]$ is the synchronisation vector defined by
 %
 \begin{equation}
-  \label{eq:trig:encoding}
-  (y_1 \lor \dots \lor y_m \Rightarrow x) \land (x = x_1 \lor \dots
-  \lor x_n).
+  \label{eq:nopri:connector}
+  \nopri[x,g,u] \bydef{=}
+  \bigl(p(b_p,\export[A](p))\bigr)^{p \in P_x}
+  \rightarrow
+  \alpha_p
+  \left[\bigwedge R(\tau(x))\bigl[\nicefrac{b_p}{p}\bigr]\right]
+  \,,
 \end{equation}
 %
-If there are no trigger sub-connectors, \ie $n = 0$, we use the
-formula
-%
-\begin{equation}
-  \label{eq:synch:encoding}
-  x = \bigl((y_1 = y_2) \land \dots \land (y_1 = y_m)\bigr)
-\end{equation}
-%
-($x$ is equal to $\true$ if all $x_1, \dots, x_m$ are equal, it is
-equal to $\false$ otherwise).
-
-Notice that, in the flat connector example above, the formula was
-essentially the same, with $p_i$ instead of $x_i$ and $q_i$ instead of
-$y_i$, and without the additional variable $x$.  Indeed, $x$ is used
-to encode the causal dependencies between this connector and, if
-necessary, those in higher levels of the hierarchy.  The Boolean
-encoding of the causal dependencies among the ports of the entire
-connector is obtained by taking the conjunction of formulas obtained
-for each sub-connector.
-
-Consider again the connector {\NameTimer.\PortTick \trigsynch
-  (\PortFail \trigsynch \NameCtrl.\PortFail)}.  Associating the
-varaibles $b_0$, $b_1$ and $b_2$ to ports {\PortFail},
-{\NameCtrl.\PortFail} and {\NameTimer.\PortTick}, respectively, and
-variables $y_1$ and $y_2$ to the top- ({\NameTimer.\PortTick
-  \trigsynch $\cdot$}) and second-level (\PortFail \trigsynch \NameCtrl.\PortFail) connectors in the hierarchy,
-we obtain the following formula
-%
-\begin{equation}
-  \label{eq:tff:example}
-  (b_1 \Rightarrow y_2) \land (y_2 = b_0) \land (y_2 \Rightarrow y_1)
-  \land (y_1 = b_2)
-  \,.
-\end{equation}
-%
-Observe now that the top-level connector, by its very nature, does not
-have any higher level connectors and therefore we can eliminate the
-corresponding Boolean variable.  This simplifies \eq{tff:example}, to
-%
-\begin{equation}
-  \label{eq:tff:example:1}
-  (b_1 \Rightarrow y_2) \land (y_2 = b_0) \land (y_2 \Rightarrow b_2)
-  \,.
-\end{equation}
-%
-In the general case, this corresponds to replacing, \emph{for
-  top-level connectors}, equations \eq{trig:encoding} and
-\eq{synch:encoding}, respectively, by
-%
-\begin{gather}
-  \label{eq:trig:encoding:1}
-  y_1 \lor \dots \lor y_m \Rightarrow x_1 \lor \dots
-  \lor x_n
-  \\
-  \intertext{and}
-  \label{eq:synch:encoding:1}
-  (y_1 = y_2) \land \dots \land (y_1 = y_m)
-  \,.
-\end{gather}
-%
-Furthermore, in the context of one connector (or synchronisation
-vector), some interaction must be fired.  Thus, \emph{for top-level
-  connectors}, \eq{synch:encoding:1} can be further simplified to 
-%
-\begin{equation}
-  \label{eq:synch:encoding:2}
-  y_1 \land \dots \land y_m
-  \,.
-\end{equation}
+with $b_p$ a fresh Boolean variable, $\alpha_p$ a fresh name, $\tau :
+\ac(P_A) \rightarrow \ct(P_A)$ and $R : \ct(P_A) \rightarrow
+\cru(P_A)$ the two mappings defined in \app{transformations} and
+illustrated in \tab{connectors}, $\bigl[\nicefrac{b_p}{p}\bigr]$ is
+the substitution, which replaces, in the expression that preceeds it,
+all occurrences of $p$ by $b_p$.
+
+\todoLHin{The update assignment is missing from the above encoding.
+  It should be $u\bigl[\nicefrac{b_p}{p}\bigr]$, but I do not see in
+  \defn{pnets} where should I place it.  I think it is missing there.
+  \Simon}
+
+\begin{theorem}
+  The open automaton $\semopen{\nopri[A,\partition]}$ corresponding to
+  $\nopri[A,\partition]$ (see \defn{operationalSemantics}) is
+  isomorphic to the LTS $\semopen{\Gamma\bigl(\cC_A, (B_D)^{D \in
+      \partition}\bigr)}$ (see \defn{comp:semantics}), where, for each
+  $D \in \partition$, the component $B_D \bydef{=} \tuple{\{q\}, q,
+    V_D, \val{0}{D}, D, \export[D], \goesto{}}$, with
+%
+  \begin{align*}
+    V_D &= \bigcup_{p \in D} \export[A](p)
+    \,,
+    &\val{0}{D}(v) &= \bot, \text{ for all $v \in V_D$}
+    \,,\\
+    \goesto{} &= \bsetdef{(q, p, \true, \noop, q)}{p \in D}
+    \,,
+    &\export[D](p) &= \export[A](p), \text{ for all $p \in D$}
+    \,,
+  \end{align*}
+%
+  and $q$ a fresh state.
+\end{theorem}
+%
+\begin{proof}[Sketch of a proof]
+  The theorem follows from the correctness of $\tau$ and $R$ shown in
+  \cite{BliSif10-causal-fmsd}.
+\end{proof}
+
+\noteSBin{This theorem is very probably correct: the key question is
+  whether isomorphism is, indeed, the relation to use. In absence of
+  silent transitions, must be the case.}
+
+Observe now that this encoding can be optimised to remove unnecessary
+Boolean variables and loop transitions marked by \false.  For
+instance, consider the ports shown in red in the second column of
+\tab{connectors}.  All these ports only appear in the roots of the
+corresponding causal interaction trees and, furthermore, each of these
+trees only has one root (see \app{trees}).  In such cases, as in the
+{\NameTimer.\PortTick \trigsynch (\PortFail \trigsynch
+  \NameCtrl.\PortFail)} example discussed above, the Boolean variables
+and the \false-marked loop transitions associated to these ports can
+be removed.  Furthermore, the rules associated to these ports in the
+corresponding systems of causal rules (see the rules in red in the
+third column of \tab{connectors}) become tautological and can also be
+removed from the corresponding guards in \eq{nopri:connector}.
 

### 2018-10-20 2018-Arch-pNets/arch-pNets.tex
Arch-pNets paper: Added an sketch of the encoding of maximal progress

@@
 
+\noteSBin{In order to encode the maximal progress priority model, one
+  has to introduce an additional Boolean variable, for each port (for
+  which we have introduced one in $\nopri[A, \partition]$), such that
+  $q \goesto{p(b_p, \true)} q'$ iff $\exists q'': q \goesto{p(\true)}
+  q''$ in $\nopri[A, \partition]$.  Intuitively, this variable
+  indicates whether \emph{there is a possibility to fire $p$ from the
+    same state}.  Then, in the SV guard, we have to check whether
+  \emph{all ports in $c_p(\tau(x))$ can be fired} (see
+  \app{transformations}).  If so, then $p$ must be fired, \ie
+  $p(\false)$ must be blocked.  This is pretty much straightforward,
+  but care must be taken when doing this in the general case, since
+  causal interaction trees can get pretty tricky due to $\oplus$ (see
+  \app{trees}).}
 %****************************************************************

### 2018-10-23 2016-Weak-FH-Bisim/WeakBisim.tex
Preuve reprise

@@
        \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
-         {s^1_i \OTarrow {\tau} s^1_{i}} \in \mathcal{T}  \wedge
-
-\openrule
-         {
-           \beta_j^{J^2},\Pred\,^2,\Post^2 }
+         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}  \wedge
+
+\openrule
+         {
+           {\beta_j^2}^{J^2},\Pred\,^2,\Post^2 }
          {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
@@
 \end{mathpar}
+
+For the sake of simplicity, a single tau open transition will be considered; however the proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule.
+By  Definition \ref{def-Weak-bisim} we have for an open transition:
+\begin{mathpar}
+%\inferrule{
+ \openrule
+    {
+       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
+         {s^1 \OTarrow {\tau} s'^1} \in \mathcal{T}          
+\end{mathpar}
+there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
+ \begin{mathpar}
+    \openrule
+         {
+           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {t \OTWeakarrow {\alpha_x} t_x}
+\end{mathpar}
+ such that  $\forall x,\{j\in J^2|\beta^1_j\neq\tau\}=J_{x}, (s'^1,t_x|\Pred_{s'^1,t_x})\in \mathcal{R}$. \\
+ $\Pred_{s1,t} \land \Pred_i^1\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
+   \left( \forall j\in J_x. \vis{\beta^1_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
+     \land \alpha_x\!=\!\tau \land  
+     \Pred_{s'^1,t_x}\subst{\Post_i^1}\subst{\Post_{OT_x}}\right)$
+
+And similarly, for an open transition:
+     \begin{mathpar}
+%\inferrule{
+ \openrule
+    {
+       \set{\beta^3_i},\Pred^3_i,\Post^3_i   }
+         {s^3 \OTarrow {\tau} s'^3} \in \mathcal{T}          
+\end{mathpar}
+there exist weak open transition $\symb{WOT}_z^{z\in Z} \subseteq \WT_2$:
+ \begin{mathpar}
+    \openrule
+         {
+           \gamma_{j z}^{j\in J_{z}}, \Pred_{OT_z},\Post_{OT_z}}
+         {t'' \OTWeakarrow {\alpha_x} t_z}
+\end{mathpar}
+ such that  $\forall z,\{j\in J^3|\beta^3_j\neq\tau\}=J_{3}, (s'^3,t_z|\Pred_{s'^3,t_z})\in \mathcal{R}$. \\
+ $\Pred_{s^3,t''} \land \Pred_i^3\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{z\in Z}}
+   \left( \forall j\in J_z. \vis{\beta^3_j}=\gamma_{jz}  \Rightarrow \Pred_{OT_z}
+     \land \alpha_z\!=\!\tau \land  
+     \Pred_{s'^3,t_z}\subst{\Post_i^3}\subst{\Post_{OT_z}}\right)$
+
+Concerning the middle open transition, by Definition \ref{def-Weak-bisim} we know that for each open transition $OT$ in $\mathcal{T}_1$:
+ \begin{mathpar}
+     \openrule
+         {
+           \beta_j^{J^2},\Pred\,^2,\Post^2 }
+         {s^2 \OTarrow {\alpha} s'^2} 
+\end{mathpar}
+ there exist weak open transitions $\symb{WOT}_y^{y\in Y} \subseteq \WT_2$:
+ \begin{mathpar}
+    \openrule
+         {
+           \gamma_{j y}^{j\in J_{y}}, \Pred_{OT_y},\Post_{OT_y}}
+         {t' \OTWeakarrow {\alpha_y} t_y}
+\end{mathpar}
+ such that  $\forall x,\{j\in J^2|\beta^2_j\neq\tau\}=J_{x}, (s'^2,t_y|\Pred_{s'^2,t_y})\in \mathcal{R}$; \\
+ $\Pred_{s^2,t'} \land \Pred\,^2\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}}
+   \left( \forall j\in J_y. \vis{\beta^2_j}=\gamma_{jy}  \Rightarrow \Pred_{OT_y}
+     \land \alpha\!=\!\alpha_y \land  
+     \Pred_{s'^2,t_y}\subst{\Post^2}\subst{\Post_{OT_y}}\right)$
+
+\medskip
+
+On other hand, by applying (\WTTrois)~rule  \TODO{on each  $\symb{WOT}_x$} we have:
+
+ \begin{mathpar}
+  \mprset {vskip=.5ex}
+\inferrule {
+\openrule
+         {
+           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {t \OTWeakarrow {\tau} t_x}
+\qquad
+\openrule
+         {
+           \gamma_{j y}^{j\in J_{y}}, \Pred_{OT_y},\Post_{OT_y}}
+         {t' \OTWeakarrow {\alpha_y} t_y}
+\qquad
+\openrule
+         {
+           \gamma_{j z}^{j\in J_{z}}, \Pred_{OT_z},({x_k\gets e_k})^{k\in K}}
+         {t'' \OTWeakarrow {\tau} t_z}
+\\
+\Pred=\Pred_{OT_x}\land\Pred_{OT_y}\subst{\Post_{OT_x}}\land (\Pred_{OT_z}\subst{\Post_{OT_y}})\subst{\Post_{OT_x}}
+}
+{
+\openrule
+         {
+           \gamma_{j x}^{j\in J_{x}} \dotcup \gamma_{j y}^{j\in J_{y}}\dotcup\gamma_{j z}^{j\in J_{z}},
+		\Pred,
+				({x_k\gets (e_k\subst {\Post_{OT_y}})\subst{\Post_{OT_y}}})^{k\in K} } 
+         {t \OTWeakarrow {\alpha_x} t_z} 
+} 
+ \end{mathpar}
+ such that $t_x=t' \wedge t_y=t''$
+
+\newpage
+-----------------------------------------------------
+
 The (\WTDeux)~ and (\WTTrois)~  rules can be applied repeatedly to produce:

### 2018-10-23 2016-Weak-FH-Bisim/WeakBisim.tex
rework proof

@@
 For the sake of simplicity, a single tau open transition will be considered; however the proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule.
-By  Definition \ref{def-Weak-bisim} we have for an open transition:
+
+\paragraph{1st transition}
+
+We have
 \begin{mathpar}
@@
        \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
-         {s^1 \OTarrow {\tau} s'^1} \in \mathcal{T}          
-\end{mathpar}
+         {s \OTarrow {\tau} s'^1} \in \mathcal{T}          
+\end{mathpar}
+Also, we have $(s,t|\Pred_{s,t})\in\mathcal{R}$. Then
+by  Definition \ref{def-Weak-bisim} we have for an open transition:
+
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
@@
  such that  $\forall x,\{j\in J^2|\beta^1_j\neq\tau\}=J_{x}, (s'^1,t_x|\Pred_{s'^1,t_x})\in \mathcal{R}$. \\
- $\Pred_{s1,t} \land \Pred_i^1\\
+ $\Pred_{s,t} \land \Pred_i^1\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
@@
 
-And similarly, for an open transition:
-     \begin{mathpar}
-%\inferrule{
- \openrule
-    {
-       \set{\beta^3_i},\Pred^3_i,\Post^3_i   }
-         {s^3 \OTarrow {\tau} s'^3} \in \mathcal{T}          
-\end{mathpar}
-there exist weak open transition $\symb{WOT}_z^{z\in Z} \subseteq \WT_2$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j z}^{j\in J_{z}}, \Pred_{OT_z},\Post_{OT_z}}
-         {t'' \OTWeakarrow {\alpha_x} t_z}
-\end{mathpar}
- such that  $\forall z,\{j\in J^3|\beta^3_j\neq\tau\}=J_{3}, (s'^3,t_z|\Pred_{s'^3,t_z})\in \mathcal{R}$. \\
- $\Pred_{s^3,t''} \land \Pred_i^3\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{z\in Z}}
-   \left( \forall j\in J_z. \vis{\beta^3_j}=\gamma_{jz}  \Rightarrow \Pred_{OT_z}
-     \land \alpha_z\!=\!\tau \land  
-     \Pred_{s'^3,t_z}\subst{\Post_i^3}\subst{\Post_{OT_z}}\right)$
-
-Concerning the middle open transition, by Definition \ref{def-Weak-bisim} we know that for each open transition $OT$ in $\mathcal{T}_1$:
+Note that, because $\AlgE\cap\AlgA=\emptyset$ and $\alpha_x\!=\!\tau$ we have 
+directly\NOTE{the argumet is not trivial!}:
+\begin{mathpar}
+    \openrule
+         {
+           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {t \OTWeakarrow {\tau} t_x}
+\end{mathpar}
+\paragraph{2nd transition}
+
+Concerning the middle open transition, we have
  \begin{mathpar}
@@
            \beta_j^{J^2},\Pred\,^2,\Post^2 }
-         {s^2 \OTarrow {\alpha} s'^2} 
-\end{mathpar}
- there exist weak open transitions $\symb{WOT}_y^{y\in Y} \subseteq \WT_2$:
+         {s'^1 \OTarrow {\alpha} s'^2} 
+\end{mathpar}
+For each of the WOTs obtained above, we have the following.
+We have $(s'^1,t_x|\Pred_{s'^1,t_x})\in \mathcal{R}$. Then
+ by Definition \ref{def-Weak-bisim}:
+
+ there exist weak open transitions $\symb{WOT}_{x y}^{x\in X,y\in Y} \subseteq \WT_2$:
  \begin{mathpar}
@@
            \gamma_{j y}^{j\in J_{y}}, \Pred_{OT_y},\Post_{OT_y}}
-         {t' \OTWeakarrow {\alpha_y} t_y}
-\end{mathpar}
- such that  $\forall x,\{j\in J^2|\beta^2_j\neq\tau\}=J_{x}, (s'^2,t_y|\Pred_{s'^2,t_y})\in \mathcal{R}$; \\
+         {t_x \OTWeakarrow {\alpha_y} t_{x y}}
+\end{mathpar}
+ such that  $\forall x,\{j\in J^2|\beta^2_j\neq\tau\}=J_{x}, 
+(s'^2,t_y|\Pred_{s'^2,t_{x y}})\in \mathcal{R}$; \\
  $\Pred_{s^2,t'} \land \Pred\,^2\\
@@
      \Pred_{s'^2,t_y}\subst{\Post^2}\subst{\Post_{OT_y}}\right)$
+
+ \paragraph{third  transition}
+And similarly, for an open transition:
+     \begin{mathpar}
+%\inferrule{
+ \openrule
+    {
+       \set{\beta^3_i},\Pred^3_i,\Post^3_i   }
+         {s'^2 \OTarrow {\tau} s'} \in \mathcal{T}          
+\end{mathpar}
+Additionally, for each $x$ and $y$, we have 
+$(s'^2,t_y|\Pred_{s'^2,t_{x y}})\in \mathcal{R}$
+and by Definition \ref{def-Weak-bisim}:
+
+there exist weak open transition $\symb{WOT}_{x y z}^{x,y,z\in Z} \subseteq \WT_2$:
+ \begin{mathpar}
+    \openrule
+         {
+           \gamma_{j z}^{j\in J_{z}}, \Pred_{OT_z},\Post_{OT_z}}
+         {t_{x y} \OTWeakarrow {\alpha_x} t_{x y z}}
+\end{mathpar}
+ such that  $\forall z,\{j\in J^3|\beta^3_j\neq\tau\}=J_{3}, 
+(s',t_{x y z}|\Pred_{s',t_{x y z}})\in \mathcal{R}$. \\
+ $\Pred_{s'^2,t_{x y}} \land \Pred_i^3\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{z\in Z}}
+   \left( \forall j\in J_z. \vis{\beta^3_j}=\gamma_{jz}  \Rightarrow \Pred_{OT_z}
+     \land \alpha_z\!=\!\tau \land  
+     \Pred_{s'^3,t_z}\subst{\Post_i^3}\subst{\Post_{OT_z}}\right)$
 

### 2018-10-24 2016-Weak-FH-Bisim/WeakBisim.tex
Proof toujours...

--- 2018-10-18 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 \\
-\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\subst{\Post_1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\subst{\Post^1_i}\\
+\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\subst{\biguplus_{i=0}^{n}\Post_i^1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\subst{\biguplus_{i=0}^{n}\Post^1_i}\\
 \Post=({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K}
@@
 \end{mathpar}
+where\\
+$
+s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
+\displaystyle{\gamma_j^{j\in J_1}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i}}}
+\\
+\Pred_{OT}=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\subst{\biguplus_{i=0}^{n}\Post_i^1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\subst{\biguplus_{i=0}^{n}\Post^1_i}\\
+\Post_{OT}=({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K}
+$
+
+For the sake of simplicity, a single tau open transition will be considered; however the proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule.
+
+\paragraph{1st transition:}
+
+We have
+\begin{mathpar}
+%\inferrule{
+ \openrule
+    {
+       \set{\beta^1},\Pred^1,\Post^1   }
+         {s \OTarrow {\tau} s^1} \in \mathcal{T}          
+\end{mathpar}
+Also, we have $(s,t|\Pred_{s,t})\in\mathcal{R}$. Then
+by  Definition \ref{def-Weak-bisim} we have for an open transition, there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
+ \begin{mathpar}
+    \openrule
+         {
+           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {t \OTWeakarrow {\alpha_x} t_x}
+\end{mathpar}
+ such that  $\forall x,\{j\in J^2|\beta^1_j\neq\tau\}=J_{x}, (s^1,t_x|\Pred_{s^1,t_x})\in \mathcal{R}$. \\
+ $\Pred_{s,t} \land \Pred^1\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
+   \left( \forall j\in J_x. \vis{\beta^1_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
+     \land \alpha_x\!=\!\tau \land  
+     \Pred_{s^1,t_x}\subst{\Post^1}\subst{\Post_{OT_x}}\right)$
+
+Note that, because $\AlgE\cap\AlgA=\emptyset$ and $\alpha_x\!=\!\tau$ we have 
+directly\NOTE{the argument is not trivial!}:
+\begin{mathpar}
+    \openrule
+         {
+           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {t \OTWeakarrow {\tau} t_x}
+\end{mathpar}
+\paragraph{2nd transition:} Concerning the middle open transition, we have
+ \begin{mathpar}
+     \openrule
+         {
+           \beta_j^{J^2},\Pred\,^2,\Post^2 }
+         {s^1 \OTarrow {\alpha} s^2} 
+\end{mathpar}
+For each of the WOTs obtained above, we have the following.
+We have $(s^1,t_x|\Pred_{s^1,t_x})\in \mathcal{R}$. Then
+ by Definition \ref{def-Weak-bisim} there exist weak open transitions $\symb{WOT}_{x y}^{x\in X,y\in Y} \subseteq \WT_2$:
+ \begin{mathpar}
+    \openrule
+         {
+           \gamma_{j x y}^{j\in J_{x y}}, \Pred_{OT_{x y}},\Post_{OT_{x y}}}
+         {t_x \OTWeakarrow {\alpha_{x y}} t_{x y}}
+\end{mathpar}
+ such that  $\forall x,\{j\in J^2|\beta^2_j\neq\tau\}=J_{x}, 
+(s^2,t_{x y}|\Pred_{s'^2,t_{x y}})\in \mathcal{R}$; \\
+ $\Pred_{s^1,t_x} \land \Pred\,^2\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}}
+   \left( \forall j\in J_{x y}. \vis{\beta^2_j}=\gamma_{jx y}\Rightarrow \Pred_{OT_{x y}}\land \alpha\!=\!\alpha_{x y} \land  
+     \Pred_{s^2,t_{x y}}\subst{\Post^2}\subst{\Post_{OT_{x y}}}\right)$
+
+ \paragraph{Third  transition:}
+And similarly, for an open transition:
+     \begin{mathpar}
+%\inferrule{
+ \openrule
+    {
+       \set{\beta^3},\Pred^3,\Post^3_i   }
+         {s^2 \OTarrow {\tau} s'} \in \mathcal{T}          
+\end{mathpar}
+Additionally, for each $x$ and $y$, we have 
+$(s^2,t_{x y}|\Pred_{s^2,t_{x y}})\in \mathcal{R}$
+and by Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{x y z}^{x\in X,y\in Y,z\in Z} \subseteq \WT_2$:
+ \begin{mathpar}
+    \openrule
+         {
+           \gamma_{j x y z}^{j\in J_{x y z}}, \Pred_{OT_{x y z}},\Post_{OT_{x y z}}}
+         {t_{x y} \OTWeakarrow {\alpha_{x y z}} t_{x y z}}
+\end{mathpar}
+ such that  $\forall z,\{j\in J^3|\beta^3_j\neq\tau\}=J_{3}, 
+(s',t_{x y z}|\Pred_{s',t_{x y z}})\in \mathcal{R}$. \\
+ $\Pred_{s^2,t_{x y}} \land \Pred^3\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{z\in Z}}
+   \left( \forall j\in J_z. \vis{\beta^3_j}=\gamma_{j x y z}  \Rightarrow \Pred_{OT_{x y z}}
+     \land \alpha_{x y z}\!=\!\tau \land  
+     \Pred_{s',t_{x y z}}\subst{\Post^3}\subst{\Post_{OT_{x y z}}}\right)$
+
+\medskip
+
+On other hand, by applying (\WTTrois)~rule  \TODO{on each  $\symb{WOT}_x$} we have:
+
+ \begin{mathpar}
+  \mprset {vskip=.5ex}
+\inferrule {
+\openrule
+         {
+           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {t \OTWeakarrow {\tau} t_x}
+\qquad
+\openrule
+         {
+           \gamma_{j x y}^{j\in J_{x y}}, \Pred_{OT_{x y}},\Post_{OT_{x y}}}
+         {t_x \OTWeakarrow {\alpha_{x y}} t_{x y}}
+\qquad
+\openrule
+         {
+           \gamma_{j x y z}^{j\in J_{x y z}}, \Pred_{OT_{x y z}},({x_k\gets e_k})^{k\in K}}
+         {t_{x y} \OTWeakarrow {\tau} t_{x y z}}
+\\
+\Pred_{OT_{x y z}}=\Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}}\land (\Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}})\subst{\Post_{OT_x}}
+}
+{
+\openrule
+         {
+           \gamma_{j x}^{j\in J_{x}} \dotcup \gamma_{j x y}^{j\in J_{x y}}\dotcup\gamma_{j x y z}^{j\in J_{x y z}},
+		\Pred_{OT_{x y z}},
+				({x_k\gets (e_k\subst {\Post_{OT_{x y}}})\subst{\Post_{OT_{x}}}})^{k\in K} } 
+         {t \OTWeakarrow {\alpha_{x y}} t_{x y z}} 
+} 
+ \end{mathpar}
+We need to prove:\\
+
+$\Pred_{s,t} \land \Pred_{OT}\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{z\in Z}}
+   \left( \forall j\in J_{x y z}. \gamma_j=\gamma_{j x y z}  \Rightarrow \Pred_{OT_{x y z}}
+     \land \alpha \!=\! \alpha_{x y} \land  
+     \Pred_{s',t_{x y z}}\subst{\Post_{OT}}\subst{\Post_{OT_{x y z}}}\right)$
+By knowing this:\\
+$\Pred_{OT}= \Pred^1 \wedge \Pred^2\subst{\Post^1} \wedge \Pred^3\subst{\Post^2}\subst{\Post^1}$\\
+$\Post_{OT}=\Post^3\subst{\Post^2}\subst{\Post^1}$\\
+We have:\\
+$\Pred_{s,t} \land \Pred^1\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
+   \left( \forall j\in J_x. \vis{\beta^1_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
+     \land \alpha_x\!=\!\tau \land  
+     \Pred_{s^1,t_x}\subst{\Post^1}\subst{\Post_{OT_x}}\right)\\
+\implies\\
+(\Pred_{s,t} \land \Pred^1)\wedge\Pred^2\subst{\Post^1}\\
+ \hspace{1cm} \implies\!\!\! \Big(\displaystyle{\bigvee_{x\in X}}
+   \left( \forall j\in J_x. \vis{\beta^1_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
+     \land \alpha_x\!=\!\tau \land  
+     \Pred_{s^1,t_x}\subst{\Post^1}\subst{\Post_{OT_x}}\right) \Big) \wedge\Pred^2\subst{\Post^1}   \\
+\implies\\    
+      $
+
+\newpage
+-----------------------------------------------------
+
 The (\WTDeux)~ and (\WTTrois)~  rules can be applied repeatedly to produce:

### 2018-10-31 2016-Weak-FH-Bisim/WeakBisim.tex
Proof of lemma 3 done

@@
 
+\TODO{Voir ou ajouter ceci: We introduce the notation ${\displaystyle \bigotimes_{i=1}^{n} \subst{Post_i}}$ to denote a combination of multiple substitution operations}
+
        \section{Weak FH-bisimulation lemmas and proofs}
@@
 \\
-\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\subst{\biguplus_{i=0}^{n}\Post_i^1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\subst{\biguplus_{i=0}^{n}\Post^1_i}\\
+\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2 \bigotimes_{i=0}^{n}\subst{\Post_i^1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\bigotimes_{i=0}^{n}\subst{\Post^1_i}\\
 \Post=({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K}
@@
 \\
-\Pred_2=\bigwedge_{i=0}^{n_2}\Pred^3_i\land\Pred\,^4\subst{ \biguplus_{i=0}^{n_2}\Post^3_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred\,^5_i\subst{\Post^4}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^1_i}
+\Pred_2=\bigwedge_{i=0}^{n_2}\Pred^3_i\land\Pred\,^4\bigotimes_{i=0}^{n_2}\subst{\Post^3_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred\,^5_i\subst{\Post^4}\Big)\bigotimes_{i=0}^{n_1}\subst{\Post^1_i}
 \\
-\Post_2= ({x^5_k\gets (e^5_k\subst {\Post^4})\subst{\biguplus_{i=0}^{n_2} \Post^3_i}})^{k\in K}
+\Post_2= ({x^5_k\gets (e^5_k\subst {\Post^4})\bigotimes_{i=0}^{n_2}\subst{\Post^3_i}})^{k\in K}
 $
@@
 }\\
-\displaystyle{\Pred=\bigwedge_{i=0}^{n_2}\Pred^6_i\land\Pred^7\subst{ \biguplus_{i=0}^{n_2}\Post^6_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred^6_i\subst{\Post^7}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^6_i}}
+\displaystyle{\Pred=\bigwedge_{i=0}^{n_2}\Pred^6_i\land\Pred^7\bigotimes_{i=0}^{n_2}\subst{\Post^6_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred^6_i\subst{\Post^7}\Big)\bigotimes_{i=0}^{n_1}\subst{\Post^6_i}}
 \\
-\displaystyle{\Post= ({x^8_k\gets (e^8_k\subst {\Post^7})\subst{\biguplus_{i=0}^{n_2} \Post^6_i}})^{k\in K}}
+\displaystyle{\Post= ({x^8_k\gets (e^8_k\subst {\Post^7})\bigotimes_{i=0}^{n_2}\subst{ \Post^6_i}})^{k\in K}}
 $\\
@@
 
-\begin{corollary} The definition of weak bisimulation given in  Definition \ref{def-Weak-bisim} is equivalent to the following one:
+\begin{lemma} The definition of weak bisimulation given in Definition \ref{def-Weak-bisim} is equivalent to the following one:
 
@@
 
-\end{corollary}
-\TODO{Proof in progress}
+\end{lemma}
+
 \begin{proof} 
@@
          {
-           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
+           \set{\beta^3_i},\Pred\,^3_i,  \Post^3_i  }
          {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
@@
 \\
-\Pred_{OT}=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\subst{\biguplus_{i=0}^{n}\Post_i^1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\subst{\biguplus_{i=0}^{n}\Post^1_i}\\
-\Post_{OT}=({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K}
+\Pred_{OT}=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\bigotimes_{i=0}^{n}\subst{\Post_i^1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\bigotimes_{i=0}^{n}\subst{\Post^1_i}\\
+\Post_{OT}=\biguplus_{i=0}^{m}(\Post_i^3\subst{\Post^2})\bigotimes_{i=0}^{n}\subst{\Post^1_i}
 $
 
-For the sake of simplicity, a single tau open transition will be considered; however the proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule.
-
-\paragraph{1st transition:}
-
-We have
+For the sake of simplicity, we will  restrict $n$ and $m$ to be equal to $1$, hence a single tau open transition will be considered; however the proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule.
+Consider each open transition separately:
+\begin{enumerate}
+\item First, we have
 \begin{mathpar}
@@
 \end{mathpar}
-\paragraph{2nd transition:} Concerning the middle open transition, we have
+\item Concerning the middle open transition, we have
  \begin{mathpar}
@@
 
- \paragraph{Third  transition:}
+\item 
 And similarly, for an open transition:
@@
 
+\end{enumerate}
 \medskip
 
-On other hand, by applying (\WTTrois)~rule  \TODO{on each  $\symb{WOT}_x$} we have:
+On other hand, by applying (\WTTrois)~rule  on each  $\symb{WOT}_x$ we have:
 
@@
          {
-           \gamma_{j x y z}^{j\in J_{x y z}}, \Pred_{OT_{x y z}},({x_k\gets e_k})^{k\in K}}
+           \gamma_{j x y z}^{j\in J_{x y z}}, \Pred_{OT_{x y z}}, \Post_{OT_{x y z}}}
          {t_{x y} \OTWeakarrow {\tau} t_{x y z}}
 \\
-\Pred_{OT_{x y z}}=\Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}}\land (\Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}})\subst{\Post_{OT_x}}
+\Pred=\Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}}\land (\Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}})\subst{\Post_{OT_x}}
 }
@@
            \gamma_{j x}^{j\in J_{x}} \dotcup \gamma_{j x y}^{j\in J_{x y}}\dotcup\gamma_{j x y z}^{j\in J_{x y z}},
-		\Pred_{OT_{x y z}},
-				({x_k\gets (e_k\subst {\Post_{OT_{x y}}})\subst{\Post_{OT_{x}}}})^{k\in K} } 
+		\Pred, \Post_{OT_{x y z}}\subst {\Post_{OT_{x y}}}\subst{\Post_{OT_{x}}}}  
          {t \OTWeakarrow {\alpha_{x y}} t_{x y z}} 
@@
 We need to prove:\\
-
-$\Pred_{s,t} \land \Pred_{OT}\\
+$\Pred_{s,t} \land \Pred\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{z\in Z}}
@@
      \land \alpha \!=\! \alpha_{x y} \land  
-     \Pred_{s',t_{x y z}}\subst{\Post_{OT}}\subst{\Post_{OT_{x y z}}}\right)$
-By knowing this:\\
+     \Pred_{s',t_{x y z}}\subst{\Post_{OT}}\subst{\Post\,}\right)$
+Recall that:\\
 $\Pred_{OT}= \Pred^1 \wedge \Pred^2\subst{\Post^1} \wedge \Pred^3\subst{\Post^2}\subst{\Post^1}$\\
 $\Post_{OT}=\Post^3\subst{\Post^2}\subst{\Post^1}$\\
-We have:\\
+Let's start with the following formula.\\
 $\Pred_{s,t} \land \Pred^1\\
@@
      \land \alpha_x\!=\!\tau \land  
-     \Pred_{s^1,t_x}\subst{\Post^1}\subst{\Post_{OT_x}}\right)\\
-\implies\\
-(\Pred_{s,t} \land \Pred^1)\wedge\Pred^2\subst{\Post^1}\\
+     \Pred_{s^1,t_x}\subst{\Post^1}\subst{\Post_{OT_x}}\right)$\\
+Applying the conjunction  $\Pred^2\subst{\Post^1}$ to both sides of the implication, we get:\\  
+$(\Pred_{s,t} \land \Pred^1)\wedge\Pred^2\subst{\Post^1}\\
  \hspace{1cm} \implies\!\!\! \Big(\displaystyle{\bigvee_{x\in X}}
@@
      \land \alpha_x\!=\!\tau \land  
-     \Pred_{s^1,t_x}\subst{\Post^1}\subst{\Post_{OT_x}}\right) \Big) \wedge\Pred^2\subst{\Post^1}   \\
-\implies\\    
+     \Pred_{s^1,t_x}\subst{\Post^1}\subst{\Post_{OT_x}}\right) \Big) \wedge\Pred^2\subst{\Post^1} \subst{\Post_{OT_x}}  \\
 $
-
-\newpage
------------------------------------------------------
-
-The (\WTDeux)~ and (\WTTrois)~  rules can be applied repeatedly to produce:
-\begin{mathpar}
-%\inferrule{
- \forall i \in [0\ldots n].\openrule
-    {
-       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
-         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}          \implies
- \openrule
-         {
-           \set{\gamma_1},\Pred_1,\Post_1   }
-         {s \OTWeakarrow {\tau} s_1} \in\! \WT 
-\end{mathpar}
-where 
-\begin{mathpar}
-s=s^1_0 \wedge s^1_{n}\!=s_1,
-\displaystyle{\set{\gamma_1}=\mybigdotcup_{i=0}^{n} \vis{\set{\beta^1_i}}}, 
-\Pred_1\!=\!\bigwedge_{i=0}^{n}\Pred^1_i, \Post_1= \biguplus_{i=0}^{n} \Post_i^1\\
-\end{mathpar}
-And similarly, a series of $m$ open transitions can be simplified:
-\begin{mathpar}
-%\inferrule{
-\forall i \in [0\ldots m].\openrule
-         {
-           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\!\gets e^3_k})^{k\in K}    }
-         {s^3_i \OTarrow {\tau} s^3_{i+1}}\! \in\! \mathcal{T}       
-          \!\implies\!
-\openrule
-         {
-           \set{\gamma_3},\Pred_3, ({x_k\!\gets e_k})^{k\in K}}
-         {s_2 \OTWeakarrow {\tau} s'}\! \in\! \WT 
-\end{mathpar}
-where 
-\begin{mathpar}
-s_2=s^3_0 \wedge s^3_{m}\!=s',
-\displaystyle{\set{\gamma_3}=\mybigdotcup_{i=0}^{m} \vis{\set{\beta^3_i}}}, 
-\Pred_3\!=\!\bigwedge_{i=0}^{m}\Pred^3_i 
-%\Post_3= \biguplus_{i=0}^{n_1} \Post_i^1\\
-\end{mathpar}
-Concerning the middle open transition, by Definition \ref{def-Weak-bisim} we know that for each open transition $OT$ in $\mathcal{T}_1$:
- \begin{mathpar}
-     \openrule
-         {
-           \beta_j^{J^2},\Pred\,^2,\Post^2 }
-         {s^2 \OTarrow {\alpha} s'^2} 
-\end{mathpar}
- there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {t \OTWeakarrow {\alpha_x} t_x}
-\end{mathpar}
- such that  $\forall x,J^2=J_{x}, (s'^2,t_x|\Pred_{s'^2,t_x})\in \mathcal{R}$; 
- and  \TODO{$\{j\in J^2|\beta_j\neq\tau\}$ useless} \\
- $\Pred \land \Pred\,^2\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
-   \left( \forall j\in J_x. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
-     \land \alpha\!=\!\alpha_x \land  
-     \Pred_{s'^2,t_x}\subst{\Post^2}\subst{\Post_{OT_x}}\right)$
-
-\medskip
-
-On other hand, by applying (\WTTrois)~rule  on each  $\symb{WOT}_x$ we have:
-
- \begin{mathpar}
-  \mprset {vskip=.5ex}
-\inferrule {\openrule
-         {
-           \set{\gamma_1},\Pred_1,\Post_1   }
-         {s \OTWeakarrow {\tau} s_1} 
-\qquad
-\openrule
-         {
-           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {t \OTWeakarrow {\alpha_x} t_x}
-\qquad
-\openrule
-         {
-           \set{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
-         {s_2 \OTWeakarrow {\tau} s'} 
-\\
-\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_{OT_x}})\subst{\Post_1}
-}
-{
-\openrule
-         {
-           \set{\gamma_1}\dotcup\gamma_{j x}^{j\in J_{x}} \dotcup\set{\gamma_3},
-		\Pred,
-				({x_k\gets (e_k\subst {\Post_{OT_x}})\subst{\Post_1}})^{k\in K} } 
-         {s \OTWeakarrow {\alpha_x} s'} 
-} 
- \end{mathpar}
-such that
-$s_1=t \wedge t_x=s_2$  \TODO{Attention les states; I'm not convinced}\\
-Therefore, we can deduce that:
-
-For any open transition $\symb{WOT}$ in $\WT_1$:
- \begin{mathpar}
-     \openrule
-         {
-           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
-         {s \OTWeakarrow {\alpha} s'}
-
-\end{mathpar}
- there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
- \begin{mathpar}
- {
-\openrule
-         {
-           \set{\gamma_1}\dotcup\gamma_{j x}^{j\in J_{x}} \dotcup\set{\gamma_3},
-		\Pred,
-				({x_k\gets (e_k\subst {\Post_{OT_x}})\subst{\Post_1}})^{k\in K} } 
-         {s \OTWeakarrow {\alpha_x} s'} 
-}     
-\end{mathpar}
-\TODO{Side Conditions to discuss}\\
- such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
- and  \\
-$\Pred \land \Pred_{OT}\\
-\displaystyle{\implies\!\!\! \bigvee_{x\in X}
-   \left( \forall j\in J_x.\gamma_j=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
-     \land \alpha\!=\!\alpha_x \land  
-     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)}$
-
-\noindent ($\Leftarrow$) Now, we prove that the definition above implies Definition \ref{def-Weak-bisim}.
-
-Suppose that for any weak open transition $\symb{WOT}$ in $\WT_1$:
- \begin{mathpar}
-     \openrule
-         {
-           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
-         {s \OTWeakarrow {\alpha} s'}
-
-\end{mathpar}
- there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {t \OTWeakarrow {\alpha_x} t_x}
-\end{mathpar}
- such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
- and  \\
-$\Pred \land \Pred_{OT}\\
-\displaystyle{\implies\!\!\! \bigvee_{x\in X}
-   \left( \forall j\in J_x.\gamma_j=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
-     \land \alpha\!=\!\alpha_x \land  
-     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)}$
-
-and suppose that we have:
-\begin{mathpar}
-     \openrule
-         {
-           \beta_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
-         {s \OTarrow {\alpha} s'}
-
-\end{mathpar}
-
-By applying (\WTDeux)~rule we can directly deduce that we have:
-
-\begin{mathpar}
-     \openrule
-         {
-           \vis{\beta_j^{j\in J_1}},\Pred_{OT},\Post_{OT}}
-         {s \OTWeakarrow {\alpha} s'}
-
-\end{mathpar}
-
-Then by transitivity,   it is straightforward to  deduce that for any open transition $\symb{OT}$ in $\mathcal{T}_1$:
- \begin{mathpar}
-     \openrule
-         {
-           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
-         {s \OTarrow {\alpha} s'}
-
-\end{mathpar}
- there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {t \OTWeakarrow {\alpha_x} t_x}
-\end{mathpar}
- such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
- and  \\
-$\Pred \land \Pred_{OT}\\
-\displaystyle{\implies\!\!\! \bigvee_{x\in X}
-   \left( \forall j\in J_x.\vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
-     \land \alpha\!=\!\alpha_x \land  
-     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)}$
-
+Note because of the domain independence of the substitution, we have just added  $\subst{\Post_{OT_x}}$ on the right side. A little rewriting gives:\\
+$(\Pred_{s,t} \land \Pred^1)\wedge\Pred^2\subst{\Post^1}\\
+ \hspace{1cm} \implies\!\!\! \Big(\displaystyle{\bigvee_{x\in X}}
+   \left(\forall j\in J_x. \vis{\beta^1_j}\!=\!\gamma_{jx}\Rightarrow \Pred_{OT_x}
+     \!\land\! \alpha_x\!=\!\tau\land(\Pred_{s^1,t_x}\wedge\Pred^2)\subst{\Post^1}\subst{\Post_{OT_x}} \right)\Big)$\\
+By replacing $(\Pred_{s^1,t_x}\wedge\Pred^2)$ sub-term, so the formula becomes: \\
+$(\Pred_{s,t} \land \Pred^1)\wedge\Pred^2\subst{\Post^1}\\
+ \hspace{1cm} \implies\!\!\! \Big(\displaystyle{\bigvee_{x\in X}}
+   (\forall j\in J_x. \vis{\beta^1_j}\!\!=\!\!\gamma_{jx}  \Rightarrow \Pred_{OT_x}
+     \!\land\! \alpha_x\!=\!\tau \land \Big(\displaystyle{\bigvee_{y\in Y}}
+   ( \forall j\in J_{x y}.
+\vis{\beta^2_j}\!\!=\!\!\gamma_{jx y}\Rightarrow \Pred_{OT_{x y}}\land \alpha\!=\!\alpha_{x y} \land \Pred_{s^2,t_{x y}}\subst{\Post^2}\subst{\Post_{OT_{x y}}})\Big)\subst{\Post^1} \subst{\Post_{OT_x}} )\Big)$\\
+Furthermore, the rewriting of the implication will give:\\
+$(\Pred_{s,t} \land \Pred^1)\wedge\Pred^2\subst{\Post^1}\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} 
+\Big(\forall j\in J_x.
+\vis{\beta^1_j}\!\!=\!\!\gamma_{jx} \land  \forall j \in J_{x y}.
+\vis{\beta^2_j}\!\!=\!\!\gamma_{jx y}\Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post^1} \subst{\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \land \Pred_{s^2,t_{x y}}\subst{\Post^2}\subst{\Post^1}\subst{\Post_{OT_{x y}}} \subst{\Post_{OT_x}}\Big)$\\
+Finally, applying the conjunction $\Pred^3\subst{\Post^2}\subst{\Post^1}$ to both sides of the implication and rewriting, we get:\\
+$(\Pred_{s,t} \land \Pred^1)\wedge\Pred^2\subst{\Post^1} \land \Pred^3\subst{\Post^2}\subst{\Post^1}\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} 
+\Big(\forall j\in J_x.\vis{\beta^1_j}\!=\!\gamma_{jx} \land  \forall j \in J_{x y}.
+\vis{\beta^2_j}\!=\!\gamma_{jx y} \Rightarrow \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \alpha_x\!=\!
+\tau \land \alpha\!=\! \alpha_{x y} \land (\Pred_{s^2,t_{xy}} \land  \Pred^3) \subst{\Post^2}
+\subst{\Post^1}\subst{\Post_{OT_{x y}}} 
+\subst{\Post_{OT_x}} \Big)$\\ 
+Note because of the domain independence of the substitution, we have deleted $\subst{\Post^1}$, and  we have added  $\subst{\Post_{OT_{x y}}}\subst{\Post_{OT_x}}$ on the right side sub-terms.
+By replacing $(\Pred_{s^2,t_{xy}} \land  \Pred^3)$, we get:\\
+$(\Pred_{s,t} \land \Pred^1)\land \Pred^2\subst{\Post^1} \land \Pred^3\subst{\Post^2}\subst{\Post^1}\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} \displaystyle{\bigvee_{z\in Z}} 
+\Big(\forall j\in J_x.\vis{\beta^1_j}\!\!=\!\!\gamma_{jx} \land  \forall j \in J_{x y}.
+\vis{\beta^2_j}\!\!=\!\!\gamma_{jx y} \forall j\in J_{x y z}.
+\vis{\beta^3_j}\!\!=\!\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}} \subst{\Post_{OT_x}} \land \alpha_x\!=\!
+\tau \land \alpha\!=\!\alpha_{x y} \land \alpha_{x y z}\!=\!\tau \land \Pred_{s',t_{x y z}}  \underbrace{\subst{\Post^3}\subst{\Post^2}
+\subst{\Post^1}}_{\subst{\Post_{OT}}}\subst{\Post_{OT_{x y z}}}\subst{\Post_{OT_{x y}}} \subst{\Post_{OT_x}} \Big)$
+Therefore, we conclude:\\
+$(\Pred_{s,t} \land \Pred^1)\land \Pred^2\subst{\Post^1} \land \Pred^3\subst{\Post^2}\subst{\Post^1}\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} \displaystyle{\bigvee_{z\in Z}} 
+\Big(\forall j\in J_{x y z}.
+\vis{\beta^1_j}.\vis{\beta^2_j}.\vis{\beta^3_j}\!=\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}} \subst{\Post_{OT_x}} \land \alpha\!=\!\alpha_{x y} \land \Pred_{s',t_{x y z}}\subst{\Post_{OT}}\subst{\Post_{OT_{x y z}}}\subst{\Post_{OT_{x y}}} \subst{\Post_{OT_x}} \Big)$
+This is exactly what we needed to prove. \qed
 \end{proof}
-------------------------------------------------------
-\begin{lemma}
-Let $A_1 = <J,\mathcal{S}_1, s_0,
-    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata.
-Let $<J,\mathcal{S}_1, s_0,
-    \WT_1>$ and $<J,\mathcal{S}_2,t_0,  \WT_2>$ be the
-weak open automata derived from $A_1$ and $A_2$ respectively.
-If $A_1$ and $A_2$ are weak FH-bisimilar then 
-\begin{itemize}
- \item  For any weak open transition $\symb{WOT} \in \WT_1$:
- \begin{mathpar}
-     \openrule
-         {
-           \gamma_j^{j\in J},\Pred_{OT},\Post_{OT}}
-         {s \OTWeakarrow {\alpha} s'}
-
-\end{mathpar}
-
-there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {t \OTWeakarrow {\alpha_x} t_x}
-\end{mathpar}
- such that  $\forall x, J=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
- and  \\
- $\Pred \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-   \left( \forall j\in J_x. \gamma_j=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
-     \land \alpha\!=\!\alpha_x \land  
-     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
-
-\end{itemize}
-\end{lemma}
-
-\TODO{moved from body}
 
 \begin{theorem}[Weak FH-Bisimulation is an equivalence]\label{thm-weak-equiv} Suppose $\mathcal{R}$ 
-is a weak FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
+is a weak FH-bisimulation. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
 reflexive, symmetric and transitive.
@@
 
----------------------------------------------------------------------
+With the above lemma, we can use the same technique of Theorem \ref{thm-equiv}  to prove that a weak FH-bisimulation is an equivalence.
+Indeed, we essentially use the same proof-scheme the main difference concerns  $\beta$ and  $\gamma$.
+
+\subsection{Composition properties}
+\TODO{Ludo: in the next 2 theorems I have a doubt about the biguplus of post p : not sure they should be disjoint, but else we need to do a complex composition  of posts}
+\begin{lemma}[Weak OT decomposition]\label{lem-decompose} 
+	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
+	lemma imply that $Q$ is 
+	not a \pLTS\ but a similar lemma can be proven for a pLTS $Q$}:
+	\[ P[Q]_{j_0}  
+		\models
+		{\openrule
+			{
+				\gamma_j^{j\in J}, \Pred,  
+				\Post}
+			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
+				\ostate{s_i'^{\, i\in L}}}
+		}
+	\]
+		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.
+		 Then there exist $v_Q$, $\Pred\,'$,  
+		$\Post\,'$,   $\gamma_{j_0}=[\beta_0..\beta_n]$, and for all $p\in[0..n]$ there exist $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$.
+s.t.:\\[-2ex]
+		%\[
+		\begin{mathpar}
+		P\models{\openrule
+			{
+				\gamma_j^{j\in (J_p\setminus \Holes(Q)) \cup \{j_0\}}, 
+				\Pred\,',  
+				\Post\,'}
+			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
+				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
+		}%\]
+	\vspace{-2.2ex}\\\text{and for all $p\in[0..n]$~~}
+		%\[
+		Q\models{\openrule
+			{
+				\gamma_{p j}^{j\in J_p}, \Pred_p,  
+				\Post_p}
+			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
+				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
+		}%\]
+\\
+		\text{and~~}  \bigcup_{\begin{array}{l}
+p\in[0..n]
+\end{array}} J_{p} = J\cap\Holes(Q) \qquad
+ \text{and\qquad} \forall j\in J_p,\,\gamma_j= \mybigdotcup_{p=0}^n \gamma_{p j} \\
+ \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred \iff \Pred\,'
+		\land \!\!\bigwedge_{p=0}^n(\alpha_p=\beta_p\land \Pred_p) \qquad\text{and~}
+\Post=\Post\,'\uplus\!\! \biguplus_{p=0}^n
+		\Post_p  
+		\end{mathpar}
+where $\Post_p$ only act upon variables of 
+		$\Leaves(Q)$.
+\end{lemma}
+\TODO{proof}
+
+\begin{lemma}[Weak open transition composition]\label{lem-compose} 
+	Suppose $j_0\in J$ and $\gamma_{j_0}=[\beta_0..\beta_n]$ and additionally:\\[-2ex]
+\begin{mathpar}
+%\[
+P\models{\openrule
+	{
+		\gamma_j^{j\in J}, 
+		\Pred,  
+		\Post}
+	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
+		\ostate{s_i'^{\, i\in L}}}
+}\\
+\text{~~and for all $p\in[0..n]$~~}
+Q\models{\openrule
+	{
+		\gamma_{p j}^{j\in J_p},
+		 \Pred_p,  
+		\Post_p}
+	{\ostate{s_{p i}^{i\in L_p}} \OTWeakarrow {\alpha_p}
+		\ostate{s_{(p+1) i}^{\, i\in L_Q}}}
+}%\]
+\end{mathpar}
+Let 
+\begin{mathpar}
+J_Q=\bigcup_{\begin{array}{l}
+p\in[0..n]
+\end{array}} J_{p}
+\text{\qquad and\qquad} 
+\Pred\,'=\Pred\land   \!\!\bigwedge_{p\in[0..n]}(\alpha_p=\beta_p\land \Pred_p)
+\\
+\forall j\in J_p,\,\gamma_j= \mathop{\dot{\bigcup}}_{p\in [0..n]} \gamma_{p j}
+\end{mathpar}
+Then, we have\\[-2ex]
+	\[ P[Q]_{j_0}  
+	\models
+	{\openrule
+		{
+			\gamma_j^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
+			\Pred\,',  
+			\Post\uplus\biguplus_{p\in[0..n]}
+		\Post_p  }
+		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
+			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
+	}
+	\]
+\end{lemma}
+\TODO{proof}
+
+\TODO{prove the 3 theorems for composability of weak bisim or explain why the proof is similar to strong (thanks to the previous lemmas)}
+\newpage
+
+\TODO{Anciennement debut preuve equivalnec weak FH-bisimulation}
 
@@
   \end{small}
-
-\subsection{composition properties}
-\TODO{Ludo: in the next 2 theorems I have a doubt about the biguplus of post p : not sure they should be disjoint, but else we need to do a complex composition  of posts}
-\begin{lemma}[Weak OT decomposition]\label{lem-decompose} 
-	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
-	lemma imply that $Q$ is 
-	not a \pLTS\ but a similar lemma can be proven for a pLTS $Q$}:
-	\[ P[Q]_{j_0}  
-		\models
-		{\openrule
-			{
-				\gamma_j^{j\in J}, \Pred,  
-				\Post}
-			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
-				\ostate{s_i'^{\, i\in L}}}
-		}
-	\]
-		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.
-		 Then there exist $v_Q$, $\Pred\,'$,  
-		$\Post\,'$,   $\gamma_{j_0}=[\beta_0..\beta_n]$, and for all $p\in[0..n]$ there exist $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$.
-s.t.:\\[-2ex]
-		%\[
-		\begin{mathpar}
-		P\models{\openrule
-			{
-				\gamma_j^{j\in (J_p\setminus \Holes(Q)) \cup \{j_0\}}, 
-				\Pred\,',  
-				\Post\,'}
-			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
-				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
-		}%\]
-	\vspace{-2.2ex}\\\text{and for all $p\in[0..n]$~~}
-		%\[
-		Q\models{\openrule
-			{
-				\gamma_{p j}^{j\in J_p}, \Pred_p,  
-				\Post_p}
-			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
-				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
-		}%\]
-\\
-		\text{and~~}  \bigcup_{\begin{array}{l}
-p\in[0..n]
-\end{array}} J_{p} = J\cap\Holes(Q) \qquad
- \text{and\qquad} \forall j\in J_p,\,\gamma_j= \mathop{\dot{\bigcup}}_{p\in [0..n]} \gamma_{p j} \\
- \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred \iff \Pred\,'
-		\land \!\!\bigwedge_{p\in[0..n]}(\alpha_p=\beta_p\land \Pred_p) \qquad\text{and~}
-\Post=\Post\,'\uplus\!\! \biguplus_{p\in[0..n]}
-		\Post_p  
-		\end{mathpar}
-where $\Post_p$ only act upon variables of 
-		$\Leaves(Q)$.
-\end{lemma}
-\TODO{proof}
-
-\begin{lemma}[Weak open transition composition]\label{lem-compose} 
-	Suppose $j_0\in J$ and $\gamma_{j_0}=[\beta_0..\beta_n]$ and additionally:\\[-2ex]
-\begin{mathpar}
-%\[
-P\models{\openrule
-	{
-		\gamma_j^{j\in J}, 
-		\Pred,  
-		\Post}
-	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
-		\ostate{s_i'^{\, i\in L}}}
-}\\
-\text{~~and for all $p\in[0..n]$~~}
-Q\models{\openrule
-	{
-		\gamma_{p j}^{j\in J_p},
-		 \Pred_p,  
-		\Post_p}
-	{\ostate{s_{p i}^{i\in L_p}} \OTWeakarrow {\alpha_p}
-		\ostate{s_{(p+1) i}^{\, i\in L_Q}}}
-}%\]
-\end{mathpar}
-Let 
-\begin{mathpar}
-J_Q=\bigcup_{\begin{array}{l}
-p\in[0..n]
-\end{array}} J_{p}
-\text{\qquad and\qquad} 
-\Pred\,'=\Pred\land   \!\!\bigwedge_{p\in[0..n]}(\alpha_p=\beta_p\land \Pred_p)
-\\
-\forall j\in J_p,\,\gamma_j= \mathop{\dot{\bigcup}}_{p\in [0..n]} \gamma_{p j}
-\end{mathpar}
-Then, we have\\[-2ex]
-	\[ P[Q]_{j_0}  
-	\models
-	{\openrule
-		{
-			\gamma_j^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
-			\Pred\,',  
-			\Post\uplus\biguplus_{p\in[0..n]}
-		\Post_p  }
-		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
-			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
-	}
-	\]
-\end{lemma}
-\TODO{proof}
-
-\TODO{prove the 3 theorems for composability of weak bisim or explain why the proof is similar to strong (thanks to the previous lemmas)}
 

### 2018-11-02 modelchecker/B.java
model checker data structure

@@ -1,0 +1,7 @@
+package fr.inria.oasis.vercors.vce.openpnets.modelchecker;
+
+public class B {
+	public static final boolean TRUE = true;
+	public static final boolean FALSE = false;
+	public static final boolean DEFERRED = false;
+}

### 2018-11-02 modelchecker/Evaluation.java

@@ -1,0 +1,35 @@
+package fr.inria.oasis.vercors.vce.openpnets.modelchecker;
+
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.Expression;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.Variable;
+
+public interface Evaluation {
+	/**
+	 * The purpose of emptyEvaluation is to get the initial value
+	 */
+	public void emptyEvaluation();
+	
+	/**
+	 * update the value of the variable, like rho(x-->v)
+	 * @param evaluation
+	 * @param variable
+	 * @param expression
+	 */
+	public void update(Evaluation evaluation, Variable variable, Expression expression);
+	
+	/**
+	 * parallel update the value of variable, like rho(x-->rho(e))
+	 * @param evaluationAssignment
+	 * @param variable
+	 * @param evaluationExpression
+	 * @param expression
+	 */
+	public void parallelUpdate(Evaluation evaluationAssignment, Variable variable, Evaluation evaluationExpression, Expression expression);
+	
+	/**
+	 * apply expression, like rho(e)
+	 * @param expression
+	 * @return
+	 */
+	public Evaluation applyEvaluation(Expression expression);
+}

### 2018-11-02 modelchecker/MCGTransition.java

@@ -1,0 +1,44 @@
+package fr.inria.oasis.vercors.vce.openpnets.modelchecker;
+
+import java.util.List;
+
+public interface MCGTransition {
+
+	/**
+	 * get the target modal graph state
+	 * @return
+	 */
+	public MCGState getTargetMCGState();
+	
+	/**
+	 * set the target state
+	 * @param tarMGState
+	 */
+	public void setTargetMCGState(MCGState tarMCGState);
+	
+	/**
+	 * get the start Modal Graph state
+	 * @return
+	 */
+	public MCGState getStartMCGState();
+	
+	/**
+	 * set the start state from strMGState
+	 * @param strMGState
+	 */
+	public void setStartMCGSStart(MCGState strMCGState);
+	
+	/**
+	 * get a list of modal graph transition
+	 * @return
+	 */
+	public List<MCGTransition> getMCGTransition();
+	
+	/**
+	 * add a list of ults transition from newMGSTr
+	 * @param newMGSTr
+	 */
+	public void addMCGTransition(MCGTransition mcgTransition);
+	
+	
+}

### 2018-11-02 modelchecker/ModalGraphState.java

@@ -1,0 +1,65 @@
+package fr.inria.oasis.vercors.vce.openpnets.modelchecker;
+
+import java.util.List;
+
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.Expression;
+
+public interface ModalGraphState {
+	
+	
+	/**
+	 * set the fix point type
+	 * @param fixPointtype
+	 */
+	public void setFixPointType(String fixPointtype);
+	
+	/**
+	 * get fix point type
+	 * @return
+	 */
+	public String getFixPointType();
+	
+	/**
+	 * set the depth 
+	 * @param depth
+	 */
+	public void setDepth(int depth);
+	
+	/**
+	 * get depth
+	 * @return
+	 */
+	public int getDepth();
+	
+	/**
+	 * set operator from operator
+	 * @param operator
+	 */
+	public void setOperator(Expression operator);
+	
+	/**
+	 * get operator expression
+	 * @return
+	 */
+	public Expression getOperator();
+	
+	
+	/**
+	 * add a modal graph transition to the list of modal graph transition.
+	 * @param modalGraphTransition
+	 */
+	public void addModalGraphTransition(ModalGraphTransition modalGraphTransition);
+	
+	/**
+	 * get a list of transition from the current modal graph state
+	 * @return
+	 */
+	public List<ModalGraphTransition> getModalGraphTransition();
+	
+	/**
+	 * set a list of transitions for the current state. 
+	 * @param modalGraphTransitions
+	 */
+	public void setModalGraphTransition(List<ModalGraphTransition> modalGraphTransitions);
+	
+}

### 2018-11-02 modelchecker/ModalGraphTransition.java

@@ -1,0 +1,39 @@
+package fr.inria.oasis.vercors.vce.openpnets.modelchecker;
+
+import java.util.List;
+
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.Variable;
+
+public interface ModalGraphTransition {
+
+	/**
+	 * get target state
+	 * @return
+	 */
+	public ModalGraphState getTargetMGState();
+	
+	/**
+	 * set the target state from mgState
+	 * @param mgState
+	 */
+	public void setTargetMGState(ModalGraphState mgState);
+	
+	
+	/**
+	 * get the start modal graph state
+	 * @return
+	 */
+	public ModalGraphState getStartMGState();
+	
+	/**
+	 * set the start modal graph state
+	 * @param mgState
+	 */
+	public void setStartMGState(ModalGraphState mgState);
+	
+	/**
+	 * compute the variables
+	 * @return
+	 */
+	public List<Variable> computeVariables();
+}

### 2018-11-02 modelchecker/ULTS.java

@@ -1,0 +1,70 @@
+package fr.inria.oasis.vercors.vce.openpnets.modelchecker;
+
+import java.util.HashMap;
+import java.util.List;
+
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.Expression;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.Variable;
+
+public interface ULTS {
+	
+	/**
+	 * get a list of states
+	 * @return
+	 */
+	public List<ULTSState> getULTSStates();
+	
+	/**
+	 * get the initial state
+	 * @return
+	 */
+	public ULTSState getInitialULTSState();
+	
+	/**
+	 * Set the ultsState as the initial state
+	 * @param ultsState
+	 */
+	public void setInitialULTSState(ULTSState ultsState);
+	
+	/**
+	 * add a ULTS state
+	 * @param ultsState
+	 */
+	public void addULTSState(ULTSState ultsState);
+	
+	/**
+	 * set a set of the variables for the ULTS state
+	 * @param uLTSStateVar
+	 * @param exprList
+	 */
+	public void setStateVariables(HashMap<Variable, ULTSState> uLTSStateVar, List<Expression> exprList);
+	
+	/**
+	 * set a list of the ULTS state variables
+	 * @param varList
+	 * @param ulStateList
+	 * @param exprList
+	 */
+	public void setStateVariables(List<Variable> varList, List<ULTSState> ulStateList, List<Expression> exprList);
+	
+	/**
+	 * add a ULTS state variable
+	 * @param variable
+	 * @param ultsState
+	 * @param expr
+	 */
+	public void addStateVariable(Variable var, ULTSState ultsState, Expression expr);
+	
+	/**
+	 * get a list of variable in the ULTS state 
+	 * @return
+	 */
+	public HashMap<Variable, ULTSState> getStateVariableList();
+	
+	/**
+	 * rewrite toString()
+	 * @return
+	 */
+	public String toString();
+	
+}

### 2018-11-02 modelchecker/ULTSTransition.java

@@ -1,0 +1,59 @@
+package fr.inria.oasis.vercors.vce.openpnets.modelchecker;
+
+import java.util.List;
+
+import fr.inria.oasis.vercors.vce.pnetsmodel.ParamAction;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.Assignment;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.Expression;
+
+public interface ULTSTransition {
+
+	/**
+	 * get the target ULTS state
+	 * @return
+	 */
+	public ULTSState getTargetULTSState();
+	
+	/**
+	 * set the target state
+	 * @param ultsState
+	 */
+	public void setTargetULTSState(ULTSState tarUltsState);
+	
+	/**
+	 * get the guard in the transition
+	 * @return
+	 */
+	public Expression getGuard();
+	
+	/**
+	 * set a guard by the expr
+	 * @param expr
+	 */
+	public void setGuard(Expression expr);
+	
+	/**
+	 * get action in the ults transition
+	 * @return
+	 */
+	public Expression getAction();
+	
+	/**
+	 * set the parameterized action
+	 * @param pAction
+	 */
+	public void setAction(Expression pAction);
+	
+	/**
+	 * get a list of assignments
+	 * @return
+	 */
+	public List<Assignment> getAssignment();
+	
+	/**
+	 * set a list of assignments from assignList
+	 * @param assignList
+	 */
+	public void setAssignment(List<Assignment> assignList);
+	
+}

### 2018-11-02 modelchecker/impl/Algorithm.java

@@ -1,0 +1,246 @@
+package fr.inria.oasis.vercors.vce.openpnets.modelchecker.impl;
+
+import java.util.ArrayList;
+
+import fr.inria.oasis.vercors.vce.extension.StdNAryOperator;
+import fr.inria.oasis.vercors.vce.extension.impl.ActionLiteralImpl;
+import fr.inria.oasis.vercors.vce.extension.impl.StdNAryOpExpressionImpl;
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.impl.ModalGraphImpl.ModalGraphStateImpl;
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.impl.ModelCheckingGraphImpl.MCGStateImpl;
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.impl.ULTSImpl.ULTSStateImpl;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.AssignLeft;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.AssignRight;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.Assignment;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.BinaryOperator;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.Expression;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.Variable;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.impl.BinaryOpExpressionImpl;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.impl.BoolLiteralImpl;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.impl.VariableImpl;
+
+public class Algorithm {
+	//global variables
+	protected MCGStateImpl state;
+	protected ULTSStateImpl uState;
+	protected ModalGraphStateImpl modalGraphState;
+	protected boolean stateB;
+	protected MCGStateImpl[] stateD;
+	protected StackArray stackArray;
+	ModelCheckingGraphImpl modelCheckingGraph = new ModelCheckingGraphImpl();
+	
+	Expression be = new BoolLiteralImpl();
+	boolean B;
+	
+	/**
+	 * boolean modelCheck(State state)
+	 * @param state
+	 * @return state.status
+	 */
+	public boolean modelCheck(MCGStateImpl state) {
+		state.status = visited(state.sigma);
[…]

### 2018-11-02 modelchecker/impl/ModalGraphStateImpl.java

@@ -1,0 +1,90 @@
+package fr.inria.oasis.vercors.vce.openpnets.modelchecker.impl;
+
+import java.util.ArrayList;
+import java.util.List;
+
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.ModalGraphState;
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.ModalGraphTransition;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.Expression;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.Variable;
+
+/**
+ * comment: The structure of the label of State
+ * There are four parameters: variable, operator, depth and fixPointType
+ */
+public class ModalGraphStateImpl implements ModalGraphState{
+	protected List<Variable> varList;// The variables of the state
+	protected List<ModalGraphTransition> mgTrList;
+	
+	protected Expression operator; //The operators
+	protected int depth;				//depth
+	protected String fixPointType;	//fix point type
+	
+	public ModalGraphStateImpl(List<Variable> varList, Expression operator, int depth, String fixPointType) {
+		this.varList = varList;
+		this.operator = operator;
+		this.depth = depth;
+		this.fixPointType = fixPointType;
+	}
+	
+	public ModalGraphStateImpl(Expression operator, int depth, String fixPointType) {
+		this.operator = operator;
+		this.depth = depth;
+		this.fixPointType = fixPointType;
+	}
+
+
+	@Override
+	public void addModalGraphTransition(ModalGraphTransition mgTransition) {
+		if (mgTrList == null) {
+			this.mgTrList = new ArrayList<ModalGraphTransition>();
+		}
+		mgTrList.add(mgTransition);
+	}
+
+
+	@Override
+	public List<ModalGraphTransition> getModalGraphTransition() {
+		if (this.mgTrList == null) {
+			this.mgTrList = new ArrayList<ModalGraphTransition>();
+		}
+		return mgTrList;
+	}
+
+
+	@Override
+	public void setModalGraphTransition(List<ModalGraphTransition> modalGraphTransitions) {
+		this.mgTrList = modalGraphTransitions;
+		
+	}
+
+	@Override
+	public void setFixPointType(String fixPointtype) {
+		this.fixPointType = fixPointtype;
+	}
+
+	@Override
+	public String getFixPointType() {
+		return fixPointType;
+	}
+
+	@Override
+	public void setDepth(int depth) {
[…]

### 2018-11-02 modelchecker/impl/ModelCheckingGraphImpl.java

@@ -1,0 +1,43 @@
+package fr.inria.oasis.vercors.vce.openpnets.modelchecker.impl;
+
+
+import java.util.List;
+
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.MCGState;
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.MCGTransition;
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.ModelCheckingGraph;
+
+public class ModelCheckingGraphImpl implements ModelCheckingGraph{
+
+	//fields
+	protected List<MCGState> mcgStateList;
+	protected boolean stateB;
+	protected MCGStateImpl[] stateD;
+	protected MCGState initialMCGState;
+	protected List<MCGTransition> mcgTrList;
+	
+	public ModelCheckingGraphImpl() {
+		mcgStateList = null;
+	}
+
+	@Override
+	public MCGState getInitState() {
+		return initialMCGState;
+	}
+
+	@Override
+	public void setInitState(MCGState initialMCGState) {
+		this.initialMCGState = initialMCGState;
+	}
+
+	@Override
+	public List<MCGState> getGlobalMCGState() {
+		return mcgStateList;
+	}
+
+	@Override
+	public List<MCGTransition> getMCGTransition() {
+		return mcgTrList;
+	}
+	
+}

### 2018-11-02 modelchecker/impl/OpExpressionImpl.java

@@ -1,0 +1,204 @@
+package fr.inria.oasis.vercors.vce.openpnets.modelchecker.impl;
+
+import java.lang.reflect.InvocationTargetException;
+
+import org.eclipse.emf.common.notify.Adapter;
+import org.eclipse.emf.common.notify.Notification;
+import org.eclipse.emf.common.util.EList;
+import org.eclipse.emf.common.util.TreeIterator;
+import org.eclipse.emf.ecore.EClass;
+import org.eclipse.emf.ecore.EObject;
+import org.eclipse.emf.ecore.EOperation;
+import org.eclipse.emf.ecore.EReference;
+import org.eclipse.emf.ecore.EStructuralFeature;
+import org.eclipse.emf.ecore.resource.Resource;
+
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.AssignRight;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.BinaryOperator;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.Expression;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.Variable;
+
+public class OpExpressionImpl implements Expression{
+
+	BinaryOperator binaryOperator;
+	
+	
+	public BinaryOperator getBinaryOperator() {
+		return binaryOperator;
+	}
+
+	public void setBinaryOperator(BinaryOperator binaryOperator) {
+		this.binaryOperator = binaryOperator;
+	}
+
+	public OpExpressionImpl(BinaryOperator binaryOperator) {
+		// TODO Auto-generated constructor stub
+		this.binaryOperator = binaryOperator;
+	}
+	
+	public OpExpressionImpl() {
+		// TODO Auto-generated constructor stub
+	}
+	
+	@Override
+	public String toString() {
+		return binaryOperator.getName();
+	}
+	
+	@Override
+	public EList<Variable> getVariables() {
+		// TODO Auto-generated method stub
+		return null;
+	}
+
+	@Override
+	public EClass eClass() {
+		// TODO Auto-generated method stub
+		return null;
+	}
+
+	@Override
+	public Resource eResource() {
+		// TODO Auto-generated method stub
+		return null;
+	}
+
+	@Override
+	public EObject eContainer() {
+		// TODO Auto-generated method stub
+		return null;
+	}
+
+	@Override
+	public EStructuralFeature eContainingFeature() {
+		// TODO Auto-generated method stub
+		return null;
+	}
+
+	@Override
+	public EReference eContainmentFeature() {
[…]

### 2018-11-02 modelchecker/impl/ULTSImpl.java

@@ -1,0 +1,143 @@
+package fr.inria.oasis.vercors.vce.openpnets.modelchecker.impl;
+
+
+import java.util.ArrayList;
+import java.util.HashMap;
+import java.util.Iterator;
+import java.util.List;
+
+
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.ULTS;
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.ULTSState;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.Expression;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.Variable;
+
+public class ULTSImpl implements ULTS{
+	
+	//field
+	protected List<Variable> varList;
+	protected List<ULTSState> uLtsStates;
+	protected ULTSState initialState;
+	protected HashMap<Variable, ULTSState> ultsStateVar;
+	protected HashMap<Variable, List<Expression>> variableAssignment;
+	protected HashMap<Variable, Expression> variableInitAssignment;
+	
+	
+	public ULTSImpl() {
+		super();
+	}
+	
+	public ULTSImpl(List<ULTSState> ultsStates, ULTSState initialState, List<Variable> varList) {
+		this.uLtsStates = ultsStates;
+		this.initialState = initialState;
+		this.varList = varList;
+	}
+
+	@Override
+	public ULTSState getInitialULTSState() {
+		return initialState;
+	}
+
+	@Override
+	public void setInitialULTSState(ULTSState initUltsState) {
+		this.initialState = initUltsState;
+	}
+
+	@Override
+	public void addULTSState(ULTSState ultsState) {
+		if (this.uLtsStates == null) {
+			this.uLtsStates = new ArrayList<ULTSState>();
+		}
+		this.uLtsStates.add(ultsState);
+	}
+
+	@Override
+	public void setStateVariables(HashMap<Variable, ULTSState> uLTSStateVar, List<Expression> defaultExprList) {
+		this.ultsStateVar = new HashMap<Variable, ULTSState>();
+		this.variableAssignment = new HashMap<Variable, List<Expression>>();
+		this.variableInitAssignment = new HashMap<Variable, Expression>();
+		this.ultsStateVar.putAll(uLTSStateVar);
+		Iterator<Variable> iteVar = this.ultsStateVar.keySet().iterator();
+		int i = 0;
+		int size = defaultExprList.size();
+		while (iteVar.hasNext() && i< size) {
+			Variable variable = iteVar.next();
[…]

### 2018-11-02 modelchecker/impl/ULTSStateImpl.java

@@ -1,0 +1,70 @@
+package fr.inria.oasis.vercors.vce.openpnets.modelchecker.impl;
+
+import java.util.ArrayList;
+import java.util.List;
+
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.ULTSState;
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.ULTSTransition;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.Variable;
+
+public class ULTSStateImpl implements ULTSState{
+	
+	protected List<Variable> varList;  //The variable of a state in ULTS
+	protected List<ULTSTransition> ultsTransitions;
+	protected ULTSState ultsState;
+	
+	public ULTSStateImpl() {
+		super();
+	}
+	
+	public ULTSStateImpl(List<Variable> varList) {
+		this.varList = varList;
+	}
+	
+	public ULTSStateImpl(List<Variable> varList, List<ULTSTransition> ultsTransitions) {
+		this.varList = varList;
+		this.ultsTransitions = ultsTransitions;
+	}
+
+	@Override
+	public List<ULTSTransition> getULTransitions() {
+//		if (ultsTransitions == null) {
+//			ultsTransitions = new ArrayList<ULTSTransition>();
+//		}
+		return ultsTransitions;
+	}
+
+	@Override
+	public void addULTSTransition(ULTSTransition ultsTransition) {
+		if (this.ultsTransitions == null) {
+			this.ultsTransitions = new ArrayList<ULTSTransition>();
+		}
+		this.ultsTransitions.add(ultsTransition);
+	}
+
+	@Override
+	public void setULTSTransitions(List<ULTSTransition> ultsTransitions) {
+		this.ultsTransitions = ultsTransitions;
+	}
+
+	@Override
+	public List<Variable> getULTSStateVariables() {
+		return varList;
+	}
+
+	@Override
+	public void setULTSStateVariables(List<Variable> varList) {
+		this.varList = varList;
+	}
+
+	@Override
+	public ULTSState getULTSStateName() {
+		return ultsState;
+	}
+
+	@Override
+	public void setULTSStateName(ULTSState ultsState) {
+		this.ultsState = ultsState;
+	}
+	
+}

### 2018-11-02 modelchecker/impl/ULTSTransitionImpl.java

@@ -1,0 +1,75 @@
+package fr.inria.oasis.vercors.vce.openpnets.modelchecker.impl;
+
+import java.util.ArrayList;
+import java.util.List;
+
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.ULTSState;
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.ULTSTransition;
+import fr.inria.oasis.vercors.vce.pnetsmodel.ParamAction;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.Assignment;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.Expression;
+
+
+public class ULTSTransitionImpl implements ULTSTransition{
+	protected ULTSState targetULTSState;	  //The successor state of the transition
+	
+	protected Expression booleanExpression;				//The guard of the transition
+	protected List<Assignment> assignment;		//the assignment
+	protected Expression operator;		//the parameterized action
+	
+	public ULTSTransitionImpl() {
+		super();
+		assignment = new ArrayList<Assignment>();
+	}
+	
+	public ULTSTransitionImpl(Expression operator, ULTSState targetULTSState) {
+		super();
+		this.assignment = new ArrayList<Assignment>();
+		this.targetULTSState = targetULTSState;
+		this.operator = operator;
+	}
+
+	@Override
+	public ULTSState getTargetULTSState() {
+		if (this.targetULTSState == null) {
+			this.targetULTSState = new ULTSStateImpl();
+		}
+		return targetULTSState;
+	}
+
+	@Override
+	public void setTargetULTSState(ULTSState tarULTSState) {
+		this.targetULTSState = tarULTSState;
+	}
+
+	@Override
+	public Expression getGuard() {
+		return booleanExpression;
+	}
+
+	@Override
+	public void setGuard(Expression expr) {
+		booleanExpression = expr;
+	}
+
+	@Override
+	public Expression getAction() {
+		return operator;
+	}
+
+	@Override
+	public void setAction(Expression operator) {
+		this.operator = operator;
+	}
+
+	@Override
+	public List<Assignment> getAssignment() {
+		return assignment;
+	}
+
+	@Override
+	public void setAssignment(List<Assignment> assignList) {
+		this.assignment = new ArrayList<Assignment>();
+		this.assignment.addAll(assignList);
+	}
+}

### 2018-11-02 modelchecker/test/ModelCheckingGraphTest.java

@@ -1,0 +1,135 @@
+package fr.inria.oasis.vercors.vce.openpnets.modelchecker.test;
+
+import java.util.ArrayList;
+import java.util.List;
+
+import fr.inria.oasis.vercors.vce.extension.StdNAryOperator;
+import fr.inria.oasis.vercors.vce.extension.impl.ActionLiteralImpl;
+import fr.inria.oasis.vercors.vce.extension.impl.StdNAryOpExpressionImpl;
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.ModalGraphState;
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.ULTSState;
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.ULTSTransition;
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.impl.ModalGraphImpl;
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.impl.ModalGraphStateImpl;
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.impl.ULTSImpl;
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.impl.ULTSStateImpl;
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.impl.ULTSTransitionImpl;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.Assignment;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.BinaryOperator;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.Expression;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.Variable;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.impl.AssignmentImpl;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.impl.BinaryOpExpressionImpl;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.impl.BoolLiteralImpl;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.impl.VariableImpl;
+
+public class ModelCheckingGraphTest {
+
+	public static void main(String[] args) {
+		// TODO Auto-generated method stub
+		ModalGraphImpl mGraph = new ModalGraphImpl();
+		List<ModalGraphState> mgStateList = new ArrayList<ModalGraphState>();
+		
+		Variable emptyVariable = new VariableImpl(null);
[…]

### 2018-11-02 modelchecker/test/ULTSTest.java

@@ -1,0 +1,105 @@
+package fr.inria.oasis.vercors.vce.openpnets.modelchecker.test;
+
+import java.util.ArrayList;
+import java.util.List;
+
+import fr.inria.oasis.vercors.vce.extension.StdNAryOperator;
+import fr.inria.oasis.vercors.vce.extension.impl.ActionLiteralImpl;
+import fr.inria.oasis.vercors.vce.extension.impl.StdNAryOpExpressionImpl;
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.ULTS;
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.ULTSState;
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.ULTSTransition;
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.impl.ULTSImpl;
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.impl.ULTSStateImpl;
+import fr.inria.oasis.vercors.vce.openpnets.modelchecker.impl.ULTSTransitionImpl;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.BinaryOperator;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.Expression;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.Variable;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.impl.BinaryOpExpressionImpl;
+import fr.inria.oasis.vercors.vce.xtext.model.vceX.impl.VariableImpl;
+
+public class ULTSTest {
+
+	public static void main(String[] args) {
+		// TODO Auto-generated method stub
+		List<Variable> varList0 = new ArrayList<Variable>();
+		List<Variable> varList1 = new ArrayList<Variable>();
+		List<Variable> varList2 = new ArrayList<Variable>();
+		List<Variable> varList3 = new ArrayList<Variable>();
+		
+		Variable emptyVariable = new VariableImpl(null);
+		Variable t = new VariableImpl("t");
+		
+		//The actions: start(t), tick, timeout
+		Expression start = new ActionLiteralImpl("start", 0);
+		Expression start_t = new StdNAryOpExpressionImpl(StdNAryOperator.FUN, start, t);
+		Expression tick = new ActionLiteralImpl("tick", 0);
+		Expression timeout = new ActionLiteralImpl("timeout", 0);
+		
[…]

### 2018-11-06 2018-Arch-pNets/arch-pNets.tex
define underlined actions + WOT lemma V2

@@
   The \texttt{EnableCompL} pNet of Fig. \ref{schema:enable-composed} has 2 controllers 
-  and 2 holes. One of its possible open-transition is:
+  and 2 holes.
+One of its possible open-transition is\footnote{Note the underlined action notation that we use to represent synchronised actions, i.e.
+actions that are the result of a synchronisation and that we declare as \emph{non-observable}.
+Those actions are only used for monitoring purposes and statement of properties but cannot be synchronised again in a synchronisation vector.
+This allows us to define a weak bisimilarity equivalence with p=compositional properties.}:
+\noteLH{underline notation might be a bit too much for this paper : see at the end if we remove it or not (will we use it?)}
 
@@
     {A1_0 \OTarrow{\underline{\delta(x4)}} A1_1}
-  $\noteSB{The underline notation did not appear until here.}
+  $
 \end{example}

### 2018-11-07 2016-Weak-FH-Bisim/WeakBisim.tex

@@
 We define $\Id(s)$ as the identity function on variables of state s.
-\begin{definition}[Non-observability of silent actions]
+\begin{definition}[Non-observability of silent actions]\label{def:Non-ObsTau}
 An open automaton $A = <J,\mathcal{S},s_0,\mathcal{T}>$ \emph{cannot observe silent actions} if and only if for all $j$ in $J$ and $s$ in $\mathcal{S}$ we have
@@
 		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.
-		 Then there exist $v_Q$, $\Pred\,'$, $\Pred\,''$, 
+		 Then there exist $\alpha_Q$, $\Pred\,'$, $\Pred\,''$, 
 		$\Post\,'$, $\Post\,''$ s.t.:\\[-2ex]
@@
 
-Using this lemma, it is straightforward to see that....
+\TODO{develop or delete this sentence} Using this lemma, it is straightforward to see that....
 
@@
 
-Note that, because $\AlgE\cap\AlgA=\emptyset$ and $\alpha_x\!=\!\tau$ we have 
-directly\NOTE{the argument is not trivial!}:
+Note that, because $\AlgE\cap\AlgA=\emptyset$  (actions and expressions are disjoint) and $\alpha_x\!=\!\tau$ we have 
+directly ($\alpha_x$ cannot be a variable, and cannot contain expressions/variables because $\tau$ has no parameter):
 \begin{mathpar}
@@
      \!\land\! \alpha_x\!=\!\tau\land(\Pred_{s^1,t_x}\wedge\Pred^2)\subst{\Post^1}\subst{\Post_{OT_x}} \right)\Big)$\\
-By replacing $(\Pred_{s^1,t_x}\wedge\Pred^2)$ sub-term, so the formula becomes: \\
+By replacing $(\Pred_{s^1,t_x}\wedge\Pred^2)$ sub-term,  the formula becomes: \\
 $(\Pred_{s,t} \land \Pred^1)\wedge\Pred^2\subst{\Post^1}\\
@@
 \vis{\beta^2_j}\!\!=\!\!\gamma_{jx y}\Rightarrow \Pred_{OT_{x y}}\land \alpha\!=\!\alpha_{x y} \land \Pred_{s^2,t_{x y}}\subst{\Post^2}\subst{\Post_{OT_{x y}}})\Big)\subst{\Post^1} \subst{\Post_{OT_x}} )\Big)$\\
-Furthermore, the rewriting of the implication will give:\\
+Furthermore, the rewriting of the implication  gives:\\
 $(\Pred_{s,t} \land \Pred^1)\wedge\Pred^2\subst{\Post^1}\\
@@
 \end{lemma}
+\LUDO{A V2 by Ludo}
+\begin{lemma}[WOT decomposition]\label{lem-wot-decompose} 
+	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
+	lemma imply that $Q$ is 
+	not a \pLTS\ but a similar lemma can be proven for a pLTS $Q$}:
+	\[ P[Q]_{j_0}  
+		\models
+		{\openrule
+			{
+				\gamma_j^{j\in J}, \Pred,  
+				\Post}
+			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
+				\ostate{s_i'^{\, i\in L}}}
+		}
+	\]
+		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e.
+$Q$ takes part in the reduction\footnote{Note that necessarily $\alpha_Q\neq \tau$ as soon as silent actions are not observable Definition~\ref{def:Non-ObsTau}.}.
+		 Then there exist $\alpha_Q$, $\Pred\,'$, $\Pred\,''$, 
+		$\Post\,'$, $\Post\,''$ s.t.:\\[-2ex]
+		%\[
+		\begin{mathpar}
+		P\models{\openrule
+			{
+				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
+				\Pred\,',  
+				\Post\,'}
+			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
+				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
+		}%\]
+	\vspace{-2.2ex}\\\text{and~~}
+		%\[
+		Q\models{\openrule
+			{
+				\gamma_j^{j\in J\cap\Holes(Q)}, \Pred\,'',  
+				\Post\,''}
+			{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
+				\ostate{s_i'^{\,i\in L_Q}}}
+		}%\]
+		\end{mathpar}
+		and  $\Pred \iff \Pred\,'
+		\land \Pred\,''\land \gamma_{j_0}=[\alpha_Q]$, $\Post=\Post\,'\uplus 
+		\Post\,''$ where $\Post\,''$ is the restriction of $\Post$ over variables of 
+		$\Leaves(Q)$.
+
+\end{lemma}
+
 \TODO{proof}

### 2018-11-08 2016-Weak-FH-Bisim/WeakBisim.tex
Skype push

@@
 Now focus on OTs of the subnets. For each $m\in I_1\uplus I_2$ we have one of the two 
-following OT\footnotemark[\thefootnote]:\\[-2ex]
+following OT\footnotemark[\thefootnote]:\\
+for $m$ in $I_1$
 \[
@@
     		\ostate{(s_i^\prime)^{i\in L_m}}}\]
-Or
+Or, $m$ in $I_2$
 \[{ \pNet_m 
@@
 
-Only elements of $I$ are useful to assert the premise for reduction of $P$; the last 
+Only elements of $I_1\backslash\{j_0\}$ and  are useful to assert the premise for reduction of $P$; the last 
 one ensures the open transition for the pNet $Q$ (note that $Q$ is at place $j_0$, and by 
@@
 \begin{lemma}[Weak OT decomposition]\label{lem-decompose} 
-	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
+	Let $\Leaves(Q)=pLTS_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
 	lemma imply that $Q$ is 
@@
 		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.
-		 Then there exist $v_Q$, $\Pred\,'$,  
-		$\Post\,'$,   $\gamma_{j_0}=[\beta_0..\beta_n]$, and for all $p\in[0..n]$ there exist $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$.
+		 Then there exist $\Pred\,'$,  
+		$\Post\,'$,   $\gamma_{j_0}=[\beta_0..\beta_n]$, and for all $p\in[0..n]$ there exist $\alpha_p$, $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$.
 s.t.:\\[-2ex]
@@
 				\Post\,''}
-			{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
+			{\ostate{s_i^{i\in L_Q}} \OTWeakarrow {\alpha_Q}
 				\ostate{s_i'^{\,i\in L_Q}}}

### 2018-11-09 2018-Arch-pNets/arch-pNets.tex
New drawing Failure Timer pNet

@@
 
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=\columnwidth]{FailureTimerPNET-v4}
+  \caption{The pNET encoding the Failure Monitor architecture (without the priority model)}
+  \label{fig:FailureTimer:pNet}
+\end{figure}
+
 \begin{figure*}[t]
@@
 We obtain the
-synchronisation vector SV0 shown in \fig{enc:nopri}, where $b_0$ and
+synchronisation vector SV0 shown in \fig{FailureTimer:pNet}, where $b_0$ and
 $b_1$ are the Boolean values associated to the actions encoding the
@@
 that, in our encoding, all three ports are present in the
-synchronisation vector.  \Fig{enc:nopri} shows
+synchronisation vector.  \Fig{FailureTimer:pNet} shows
 the four synchronisation vectors SV0\ndash SV3 corresponding to the

### 2018-11-09 2016-Weak-FH-Bisim/WeakBisim.tex

@@
 
-\begin{lemma}[OT decomposition]\label{lem-decompose} 
-	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
-	lemma imply that $Q$ is 
-	not a \pLTS\ but a similar lemma can be proven for a pLTS $Q$}:
+\begin{lemma}[OT decomposition]\label{lem-decompose} Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$}.
+	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose:
 	\[ P[Q]_{j_0}  
@@
 Consider rule \TrDeux\ in 
-       Definition~\ref{def:operationalSemantics}.
+       Definition~\ref{def:operationalSemantics}, applied to the pNet $P$.
 
@@
 
-Where $j_0\in I_1$ or $j_0\in I_2$
-We know each premise is \True for $P[Q]_{j_0}$ and try to prove the equivalent premise for 
-$P$. 
+We know each premise is \True\ for $P[Q]_{j_0}$ and try to prove the equivalent premise for 
+$P$.  $j_0\in I_1$ because $Q$ is not a pLTS.
 First, $K$ and the synchronisation vector $SV_k$ are unchanged\footnotemark (however 
@@
 
-Only elements of $I_1\backslash\{j_0\}$ and  are useful to assert the premise for reduction of $P$; the last 
+Only elements of $(I_1\uplus I_2)\backslash\{j_0\}$ and  are useful to assert the premise for reduction of $P$; the last 
 one ensures the open transition for the pNet $Q$ (note that $Q$ is at place $j_0$, and by 
 definition of the open transition 
-for $P[Q]_{j_0}$, $I'_{j_0}=I\cap L_Q$, 
+for $P[Q]_{j_0}$, 
 $L_{j_0}=L_Q$, and $J_{j_0}=	J\cap\Holes(Q)$):\\[-2ex]
@@
 the OT of $P$ we have  $I'_P=I'\setminus L_Q$, and $J'_P=J'\setminus\Holes(Q)\uplus 
-\{j_0\}$;  the predicate is 
-$\Pred\,'=\bigwedge_{m\in I_k}\Pred_m  \land \Predsv(SV_k,\alpha_m^{m\in 
-I},\beta_j^{j\in J\cup \{j_0\}},\alpha)$
-where\footnotemark[\thefootnote] $\Predsv(SV_k,\alpha_m^{m\in I},\beta_j^{j\in 
+\{j_0\}$; we denote $I'_1=I_1\setminus \{j_0\}$ the predicate is 
+$\Pred\,'=\bigwedge_{m\in I_1'\uplus I_2}\Pred_m  \land \Predsv(SV_k,\alpha_m^{m \in I'_1\uplus I_2},\beta_j^{j\in J\cup \{j_0\}},\alpha)$
+where\footnotemark[\thefootnote] $\Predsv(SV_k,\alpha_m^{m \in I'_1\uplus I_2},\beta_j^{j\in 
 J\cup 
 \{j_0\}},\alpha)\Leftrightarrow 
-\forall i\in I_k.\, \alpha_i=\alpha'_i\land \forall j \in J\cup \{j_0\}.\, 
+\forall i\in I'_1\uplus I_2.\, \alpha_i=\alpha'_i\land \forall j \in J\cup \{j_0\}.\, 
 \beta_j=\alpha'_j 

### 2018-11-12 2016-Weak-FH-Bisim/WeakBisim.tex
minor changes

@@
 composability and FH-bisimilarity.
-\begin{theorem}[Composability]
+\begin{theorem}[Composability] \label{thm-composability}
 	Consider two FH-bisimilar pNets with an arbitrary number of holes, when replacing, 
@@
 \\
-		\text{and~~}  \bigcup_{\begin{array}{l}
-p\in[0..n]
-\end{array}} J_{p} = J\cap\Holes(Q) \qquad
+		\text{and~~}  
+%\bigcup_{\begin{array}{l}
+%p\in[0..n]
+%\end{array}} 
+\bigcup_{i=0}^{n}J_{p} = J\cap\Holes(Q) \qquad
  \text{and\qquad} \forall j\in J_p,\,\gamma_j= \mybigdotcup_{p=0}^n \gamma_{p j} \\
  \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred \iff \Pred\,'
-		\land \!\!\bigwedge_{p=0}^n(\alpha_p=\beta_p\land \Pred_p) \qquad\text{and~}
-\Post=\Post\,'\uplus\!\! \biguplus_{p=0}^n
+		\land \!\!\bigwedge_{p=0}^n([\alpha_p]=\gamma_{pj_0}\land \Pred_p) \qquad\text{and~}
+\Post=\Post\,'\uplus\! \biguplus_{p=0}^n
 		\Post_p  
@@
 \end{lemma}
-\LUDO{A V2 by Ludo}
+\LUDO{A V2 by Ludo} \TODO{We will check notation  $\alpha_p=...$}
+
+\begin{proof}
+By lemma \ref{lem-rel-OT-WOT} we have: 
+\begin{mathpar}
+ P[Q]_{j_0} \models \openrule
+			{
+				\gamma_j^{j\in J}, \Pred,  
+				\Post}
+			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
+				\ostate{s_i'^{\, i\in L}}} 
+\end{mathpar}
+implies 	\\			
+$			
+	P[Q]_{j_0}	\models		
+\Big(\forall i \in [0\ldots n].\openrule
+    {
+       \set{\gamma^1_i},\Pred^1_i,\Post^1_i   }
+         {\ostate{s^1_i} \OTarrow {\tau} \ostate{s^1_{i+1}}}\, \wedge\,
+\openrule
+         {
+           \set{\gamma^2},\Pred\,^2,\Post^2 }
+         {\ostate{s^2} \OTarrow {\alpha} \ostate{s'^2}}
+\,\wedge\,
+\forall i \in [0\ldots m].\openrule
+         {
+           \set{\gamma^3_i},\Pred\,^3_i, \Post^3   }
+         {\ostate{s^3_i} \OTarrow {\tau} \ostate{s^3_{i+1}}}
+\Big) 
+$
+
+such that...\\
+
+On other hand by Theorem \ref{thm-composability} we have:
+
+\TODO{La preuve page 27 est difficile a suivre...}
+
+\end{proof}
 \begin{lemma}[WOT decomposition]\label{lem-wot-decompose} 

### 2018-11-13 2016-Weak-FH-Bisim/WeakBisim.tex
work on substitution lemmas

--- 2018-11-09 2016-Weak-FH-Bisim/WeakBisim.tex
@@
     {
-\Leaves(\mylangle \set{\pNet}, \set{\Sort}, \symb{SV}_k^{k\in 
+\Leaves(\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in 
     	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
@@
     	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2},\beta_j^{j\in J},\alpha)\\ 
-    		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
-    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
+    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
     \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
     }
-    {\mylangle \set{\pNet}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
+    {\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
     	\models
@@
 Consider rule \TrDeux\ in 
-       Definition~\ref{def:operationalSemantics}, applied to the pNet $P$.
+       Definition~\ref{def:operationalSemantics}, applied to the pNet $P[Q]_{j_0}$.
 
@@
 \begin{mathpar}
-    \mprset {vskip=1ex}
+    \mprset {vskip=.8ex}
 \inferrule
     {
-\Leaves(\mylangle \set{\pNet}, \set{\Sort}, \symb{SV}_k^{k\in 
+\Leaves(\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in 
     	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
@@
      J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
-    	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
-    	\Predsv(SV_k,\alpha_m^{m\in (I_1\uplus I_2)},\beta_j^{j\in J},\alpha)\\ 
-    		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
-    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
+    	\Pred = \bigwedge_{m\in I_1\uplus I_2}\!\! \Pred_m \land
+    	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2},\beta_j^{j\in J},\alpha)\\ 
+    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
     \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
     }
-    {\mylangle \set{\pNet}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
+    {\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
     	\models
@@
 \end{mathpar} 
-
-We know each premise is \True\ for $P[Q]_{j_0}$ and try to prove the equivalent premise for 
-$P$.  $j_0\in I_1$ because $Q$ is not a pLTS.
+%\begin{mathpar}
+%    \mprset {vskip=1ex}
+%\inferrule
+%    {
+%\Leaves(\mylangle \set{\pNet}, \set{\Sort}, \symb{SV}_k^{k\in 
+%    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
+%k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
+%\\
+%\\     	
+%	\forall m\!\!\in\!\! I_1. {\pNet_m 
+%	\models\openrule
+%    	{
+%    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
+%    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
+%    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
+%  \qquad
+%\forall m\!\!\in\!\! I_2.		{ \pNet_m 
+%    	 \models
+%    	\openrule
+%    	{\emptyset, \Pred_m, \Post_m}
+%    	{\ostate{s_m} \OTarrow {\alpha_m}
+%    		\ostate{s_m'}} }\\\\
+%     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
+%    	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
+%    	\Predsv(SV_k,\alpha_m^{m\in (I_1\uplus I_2)},\beta_j^{j\in J},\alpha)\\ 
+%    		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
+%    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
+%    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
+%    }
+%    {\mylangle \set{\pNet}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
+%    	\models
+%    	{\openrule
+%    		{
+%    		{\beta_j}^{j\in J^\prime}, \Pred, \uplus_{m\in I_1\uplus I_2} 
+%    		\Post_m}
+%    		{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
+%    			\ostate{(s_i^\prime)^{i\in L}}}
+%    	}
+%    }
+%\end{mathpar}
+
+We know each premise is \True\ for $P[Q]_{j_0}$. 
+  $j_0\in I_1$ because $Q$ is not a pLTS. We try to prove the equivalent premise for 
+$P$.
+
+\TODO{REMOVE NExT RULE : IT IS WRONG: it should have different variables, etc.}
+	\noindent
+\begin{mathpar}
+    \mprset {vskip=.8ex}
+\inferrule
+    {
+\Leaves(\mylangle {\pNet}_m^{m\in I\setminus\{j_0\}}, \set{\Sort}, \symb{SV}_k^{k\in 
+    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
+k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
+\\
+\\     	
+	\forall m\!\!\in\!\! I_1\setminus\{j_0\}. {\pNet_m 
+	\models\openrule
+    	{
+    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
+    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
+    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
+  \qquad
+\forall m\!\!\in\!\! I_2.		{ \pNet_m 
+    	 \models
+    	\openrule
+    	{\emptyset, \Pred_m, \Post_m}
+    	{\ostate{s_m} \OTarrow {\alpha_m}
+    		\ostate{s_m'}} }\\\\
+     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
+    	\Pred = \bigwedge_{m\in I_1\uplus I_2}\!\! \Pred_m \land
+    	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2},\beta_j^{j\in J},\alpha)\\ 
+    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
+    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
+    }
+    {\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
+    	\models
+    	{\openrule
+    		{
+    		{\beta_j}^{j\in J\setminus \Holes(Q)\uplus \{j_0\}}, \Pred',  \biguplus_{m\in I_1\uplus I_2} 
+    		\Post_m'}
+    		{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {\alpha}
+    			\ostate{(s_i^\prime)^{i\in L\setminus L_Q}}}
+    	}
+    }
+\end{mathpar}
+
 First, $K$ and the synchronisation vector $SV_k$ are unchanged\footnotemark (however 
@@
 Considering 
-the OT of $P$ we have  $I'_P=I'\setminus L_Q$, and $J'_P=J'\setminus\Holes(Q)\uplus 
+the OT of $P$ we have another  $J'$ that is $J'_p=J'\setminus\Holes(Q)\uplus 
 \{j_0\}$; we denote $I'_1=I_1\setminus \{j_0\}$ the predicate is 
@@
 	\]
-		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.
-		 Then there exist $\Pred\,'$,  
-		$\Post\,'$,   $\gamma_{j_0}=[\beta_0..\beta_n]$, and for all $p\in[0..n]$ there exist $\alpha_p$, $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$.
-s.t.:\\[-2ex]
+		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction. Suppose $\gamma_{j_0}=[\beta_0..\beta_n]$
+		 then there exist $\Pred\,'$,  
+		$\Post\,'$,   and for all $p\in[0..n]$ there exist $\alpha_p$, $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
 		%\[
@@
  \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred \iff \Pred\,'
-		\land \!\!\bigwedge_{p=0}^n(\alpha_p=\beta_p\land \Pred_p) \qquad\text{and~}
+		\land \!\!\bigwedge_{p=0}^n(\alpha_p= \beta_p\land \Pred_p) \qquad\text{and~}
 \Post=\Post\,'\uplus\!\! \biguplus_{p=0}^n

### 2018-11-14 2016-Weak-FH-Bisim/WeakBisim.tex
Tr2 resultant

@@
 
-\TODO{REMOVE NExT RULE : IT IS WRONG: it should have different variables, etc.}
-	\noindent
-\begin{mathpar}
-    \mprset {vskip=.8ex}
-\inferrule
-    {
-\Leaves(\mylangle {\pNet}_m^{m\in I\setminus\{j_0\}}, \set{\Sort}, \symb{SV}_k^{k\in 
-    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
-k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
-\\
-\\     	
-	\forall m\!\!\in\!\! I_1\setminus\{j_0\}. {\pNet_m 
-	\models\openrule
-    	{
-    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
-    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
-    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
-  \qquad
-\forall m\!\!\in\!\! I_2.		{ \pNet_m 
-    	 \models
-    	\openrule
-    	{\emptyset, \Pred_m, \Post_m}
-    	{\ostate{s_m} \OTarrow {\alpha_m}
-    		\ostate{s_m'}} }\\\\
-     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
-    	\Pred = \bigwedge_{m\in I_1\uplus I_2}\!\! \Pred_m \land
-    	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2},\beta_j^{j\in J},\alpha)\\ 
-    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
-    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
-    }
-    {\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
-    	\models
-    	{\openrule
-    		{
-    		{\beta_j}^{j\in J\setminus \Holes(Q)\uplus \{j_0\}}, \Pred',  \biguplus_{m\in I_1\uplus I_2} 
-    		\Post_m'}
-    		{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {\alpha}
-    			\ostate{(s_i^\prime)^{i\in L\setminus L_Q}}}
-    	}
-    }
-\end{mathpar}
-
 First, $K$ and the synchronisation vector $SV_k$ are unchanged\footnotemark (however 
@@
 leaves): $\Post=\Post\,'\uplus \Post\,''$. This concludes the 
-proof as we checked all the premises of the open transition for both $P$ and $Q$.\qed
+proof as we checked all the premises of the open transition for both $P$ and $Q$. We obtain the following reduction by the rule \TrDeux
+	\noindent
+\begin{mathpar}
+    \mprset {vskip=.8ex}
+\inferrule
+    {
+\Leaves(\mylangle {\pNet}_m^{m\in I\setminus\{j_0\}}, \set{\Sort}, \symb{SV}_k^{k\in 
+    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
+k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
+\\
+\\     	
+	\forall m\!\!\in\!\! I_1\setminus\{j_0\}. {\pNet_m 
+	\models\openrule
+    	{
+    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
+    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
+    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
+  \qquad
+\forall m\!\!\in\!\! I_2.		{ \pNet_m 
+    	 \models
+    	\openrule
+    	{\emptyset, \Pred_m, \Post_m}
+    	{\ostate{s_m} \OTarrow {\alpha_m}
+    		\ostate{s_m'}} }\\\\
+     J' = \biguplus_{m\in I_1 \setminus \{j_0\}}\!\! J_m \uplus J 	\\
+    	\Pred\,' = \bigwedge_{m\in I_1\uplus I_2\setminus\{j_0\}}\!\! \Pred_m \land
+    	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2 \setminus \{j_0\}},\beta_j^{j\in J\cup\{j_0\}},\alpha)\\ 
+    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1\setminus\{j_0\}}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
+    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
+    }
+    {\mylangle {\pNet}_m^{m\in I\setminus\{j_0\}}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
+    	\models
+    	{\openrule
+    		{
+    		{\beta_j}^{j\in J\setminus \Holes(Q)\uplus \{j_0\}}, \Pred\,',  \biguplus_{m\in I_1\setminus\{j_0\}\uplus I_2} 
+    		\Post_m}
+    		{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {\alpha}
+    			\ostate{(s_i^\prime)^{i\in L\setminus L_Q}}}
+    	}
+    }
+\end{mathpar}
+\qed
 \footnotetext{Cloning and freshness introduce alpha-conversion at many points 

### 2018-11-14 2016-Weak-FH-Bisim/WeakBisim.tex
Proof of lemma 5

--- 2018-11-13 2016-Weak-FH-Bisim/WeakBisim.tex
@@
        Consider each premise of the open transition (constructed by \TrDeux\ in 
-Definition~\ref{def:operationalSemantics}). 
-We know each premise is \True for $P$ and try to prove the equivalent premise for 
+Definition~\ref{def:operationalSemantics}). Let $P=\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle$
+	\begin{description}
+		\item[{\TrDeux:}]
+	\end{description}
+
+	\noindent
+\begin{mathpar}
+    \mprset {vskip=.8ex}
+\inferrule
+    {
+\Leaves(\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in 
+    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
+k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
+\\
+\\     	
+	\forall m\!\!\in\!\! I_1. {\pNet_m 
+	\models\openrule
+    	{
+    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
+    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
+    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
+  \qquad
+\forall m\!\!\in\!\! I_2.		{ \pNet_m 
+    	 \models
+    	\openrule
+    	{\emptyset, \Pred_m, \Post_m}
+    	{\ostate{s_m} \OTarrow {\alpha_m}
+    		\ostate{s_m'}} }\\\\
+     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
+    	\Pred = \bigwedge_{m\in I_1\uplus I_2}\!\! \Pred_m \land
+    	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2},\beta_j^{j\in J},\alpha)\\ 
+    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
+    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
+    }
+    {\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
+    	\models
+    	{\openrule
+    		{
+    		{\beta_j}^{j\in J^\prime}, \Pred,  \biguplus_{m\in I_1\uplus I_2} 
+    		\Post_m}
+    		{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
+    			\ostate{(s_i^\prime)^{i\in L}}}
+    	}
+    }
+\end{mathpar}
+
+We know each premise is \True\ for $P$ and try to prove the equivalent premise for 
 $P[Q]_{j_0}$ (using the open transition of $Q$). 
@@
 %\end{array}\right)}\]
-the sub-pNet at position $j_0$ is the one filled by $Q$ which offers an open transition 
+the sub-pNet at position $j_0$ is the one filled by $Q$ (we define $P_{j_0}=Q$ and similarly $J_m=J_Q$, $\Pred_m=\Pred\,'$, $\Post_m=\Post\,'$,\ldots are the elements of the OT of Q) which offers an open transition
 by hypothesis, the other open transitions are immediate consequence of the open 
@@
 The set of moving leaves is the union of the moving leaves in the open transition for $P$ 
-and the ones for $Q$: 
-$I'_{PQ}= I'_P \uplus I'_Q$, similarly the moving holes are the union of the moving 
+and the ones for $Q$; similarly the moving holes are the union of the moving 
 holes, minus $j_0$: $J'_{PQ}=  J\setminus\{j_0\}\uplus J_Q$. The 
@@
 	gathers the post-conditions related to all 
-	the leaves. Finally, the composed open transition can be
-        built. \qed
+	the leaves: $\biguplus_{m\in I_1\cup\{j_0\}\uplus I_2} 
+    		\Post_m = 	\Post\uplus \Post\,'$. Finally, the composed open transition can be
+        built by \TrDeux:
+
+	\noindent
+\begin{mathpar}
+    \mprset {vskip=.8ex}
+\inferrule
+    {
+\Leaves(\mylangle {\pNet}_m^{m\in I\cup\{j_0\}}, \set{\Sort}, \symb{SV}_k^{k\in 
+    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
+k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
+\\
+\\     	
+	\forall m\!\!\in\!\! I_1\cup\{j_0\}. {\pNet_m 
+	\models\openrule
+    	{
+    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
+    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
+    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
+  \qquad
+\forall m\!\!\in\!\! I_2.		{ \pNet_m 
+    	 \models
+    	\openrule
+    	{\emptyset, \Pred_m, \Post_m}
+    	{\ostate{s_m} \OTarrow {\alpha_m}
+    		\ostate{s_m'}} }\\\\
+     J'_{PQ}=  J\setminus\{j_0\}\uplus J_Q	\\
+    	\Pred\,'' =\bigwedge_{m\in I _1\uplus I_2}\Pred_m \land \Pred\,'
+\land \Pred(SV_k,v_i^{i\in I_1\uplus I_2}\uplus(j_0\mapsto v_Q),\beta_j^{j\in 
+J},\alpha)\\ 
+    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1\cup\{j_0\}}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
+    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
+    }
+    {\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
+    	\models
+    	{\openrule
+    		{
+    		{\beta_j}^{j\in  J'_{PQ}}, \Pred\,'',  	\Post\uplus \Post\,'}
+    		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {\alpha}
+    			\ostate{(s_i^\prime)^{i\in L\uplus L_Q}}}
+    	}
+    }
+\end{mathpar}  
+ \qed
         \end{proof}
@@
 \\
-		\text{and~~}  \bigcup_{\begin{array}{l}
-p\in[0..n]
-\end{array}} J_{p} = J\cap\Holes(Q) \qquad
+		\text{and~~}  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) \qquad
  \text{and\qquad} \forall j\in J_p,\,\gamma_j= \mybigdotcup_{p=0}^n \gamma_{p j} \\
@@
 \end{lemma}
-\LUDO{A V2 by Ludo} \TODO{We will check notation  $\alpha_p=...$}
-
-\begin{proof}
-By lemma \ref{lem-rel-OT-WOT} we have: 
+\LUDO{A V2 by Ludo}
+
+\begin{proof} Suppose we have: 
 \begin{mathpar}
@@
 \end{mathpar}
-implies 	\\			
-$			
+By lemma \ref{lem-rel-OT-WOT} this implies we have: \\			
+$ \forall i \in [0\ldots n]	\,		
 	P[Q]_{j_0}	\models		
-\Big(\forall i \in [0\ldots n].\openrule
+\openrule
     {
        \set{\gamma^1_i},\Pred^1_i,\Post^1_i   }
-         {\ostate{s^1_i} \OTarrow {\tau} \ostate{s^1_{i+1}}}\, \wedge\,
-\openrule
+         {\ostate{s^1_i} \OTarrow {\tau} \ostate{s^1_{i+1}}}$
+~and~ $\forall i \in [0\ldots m] \, P[Q]_{j_0}	\models \openrule
+         {
+           \set{\gamma^3_i},\Pred\,^3_i, \Post_i^3   }
+         {\ostate{s^3_i} \OTarrow {\tau} \ostate{s^3_{i+1}}}
+$\\
+and $ P[Q]_{j_0}	\models \openrule
          {
@@
          {\ostate{s^2} \OTarrow {\alpha} \ostate{s'^2}}
-\,\wedge\,
-\forall i \in [0\ldots m].\openrule
-         {
-           \set{\gamma^3_i},\Pred\,^3_i, \Post^3   }
-         {\ostate{s^3_i} \OTarrow {\tau} \ostate{s^3_{i+1}}}
-\Big) 
+$ where\\
 $
-
-such that...\\
+s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
+\displaystyle{\gamma_j^{j\in J_1}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i}}}
+\\
+\Pred_{OT}=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\bigotimes_{i=0}^{n}\subst{\Post_i^1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\bigotimes_{i=0}^{n}\subst{\Post^1_i}\\
+\Post_{OT}=\biguplus_{i=0}^{m}(\Post_i^3\subst{\Post^2})\bigotimes_{i=0}^{n}\subst{\Post^1_i}
+$
 

### 2018-11-16 2016-Weak-FH-Bisim/WeakBisim.tex

--- 2018-11-13 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 \end{lemma}
-\LUDO{A V2 by Ludo} \TODO{We will check notation  $\alpha_p=...$}
-
-\begin{proof}
-By lemma \ref{lem-rel-OT-WOT} we have: 
+\LUDO{A V2 by Ludo}
+\newpage
+\begin{proof} Suppose we have: 
 \begin{mathpar}
@@
 \end{mathpar}
-implies 	\\			
+By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
+$ \forall i \in [0\ldots n]	\,		
+	P[Q]_{j_0}	\models		
+\openrule
+    {
+       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
+         {\ostate{s^1_i} \OTarrow {\tau} \ostate{s^1_{i+1}}}$
+~and~ $\forall i \in [0\ldots m] \, P[Q]_{j_0}	\models \openrule
+         {
+           \set{\beta^3_i},\Pred\,^3_i, \Post_i^3   }
+         {\ostate{s^3_i} \OTarrow {\tau} \ostate{s^3_{i+1}}}
+$\\
+and $ P[Q]_{j_0}	\models \openrule
+         {
+           \set{\beta^2},\Pred\,^2,\Post^2 }
+         {\ostate{s^2} \OTarrow {\alpha} \ostate{s'^2}}
+$ where\\
 $
-	P[Q]_{j_0}	\models		
-\Big(\forall i \in [0\ldots n].\openrule
-    {
-       \set{\gamma^1_i},\Pred^1_i,\Post^1_i   }
-         {\ostate{s^1_i} \OTarrow {\tau} \ostate{s^1_{i+1}}}\, \wedge\,
-\openrule
-         {
-           \set{\gamma^2},\Pred\,^2,\Post^2 }
-         {\ostate{s^2} \OTarrow {\alpha} \ostate{s'^2}}
-\,\wedge\,
-\forall i \in [0\ldots m].\openrule
-         {
-           \set{\gamma^3_i},\Pred\,^3_i, \Post^3   }
-         {\ostate{s^3_i} \OTarrow {\tau} \ostate{s^3_{i+1}}}
-\Big) 
+s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
+\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i}}}
+\\
+\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\bigotimes_{i=0}^{n}\subst{\Post_i^1}\land (\bigwedge_{i=0}^m\Pred\,^3_i\subst{\Post^2})\bigotimes_{i=0}^{n}\subst{\Post^1_i}\\
+\Post=\biguplus_{i=0}^{m}(\Post^3_i\subst{\Post^2})\bigotimes_{i=0}^{n}\subst{\Post^1_i}
 $
 
-such that...\\
-
-On other hand by Theorem \ref{thm-composability} we have:
-
-\TODO{La preuve page 27 est difficile a suivre...}
+We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$,  we have obtain of each case:
+\begin{enumerate}
+\item $P\models{\openrule
+			{
+				\beta_{ij}^{1j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
+				{\Pred_i^1}',  
+				{\Post_i^1}'}
+			{\ostate{s_{il}^{1l\in L\setminus L_Q}} \OTarrow {\tau}
+				\ostate{s_{il}'^{\,1l\in L\setminus L_Q}}}
+		}%\]
+	\,\text{and~~}
+		%\[
+		Q\models{\openrule
+			{
+				\beta_{ij}^{1j\in J\cap\Holes(Q)}, {\Pred_i^1}'',  
+				{\Post_i^1}''}
+			{\ostate{s_{il}^{1l\in L_Q}} \OTarrow {\alpha^1_Q}
+				\ostate{s_{il}'^{\,1l\in L_Q}}}
+		}%\]
+$and  $\Pred_i^1 \iff {\Pred_i^1}'
+		\land {\Pred_i^1}''\land \alpha^1_Q=\beta^1_{ij_0}$, $\Post_i^1={\Post_i^1}'\uplus 
+		{\Post_i^1}''$ where ${\Post_i^1}''$ is the restriction of $\Post_i^1$ over variables of $\Leaves(Q)$.
+\item
+ $P\models{\openrule
+			{
+				\beta_{ij}^{3j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
+				{\Pred_i^3}',  
+				{\Post_i^3}'}
+			{\ostate{s_{il}^{3l\in L\setminus L_Q}} \OTarrow {\tau}
+				\ostate{s_{il}'^{\,3l\in L\setminus L_Q}}}
+		}%\]
+	\,\text{and~~}
+		%\[
+		Q\models{\openrule
+			{
+				\beta_{ij}^{3j\in J\cap\Holes(Q)}, {\Pred_i^3}'',  
+				{\Post_i^3}''}
+			{\ostate{s_{il}^{3l\in L_Q}} \OTarrow {\alpha^3_Q}
+				\ostate{s_{il}'^{\,3l\in L_Q}}}
+		}%\]
+$and  $\Pred_i^3 \iff {\Pred_i^3}'
+		\land {\Pred_i^3}''\land \alpha^3_Q=\beta^3_{ij_0}$, $\Post_i^3={\Post_i^3}'\uplus 
+		{\Post_i^3}''$ where ${\Post_i^3}''$ is the restriction of $\Post_i^3$ over variables of $\Leaves(Q)$.
+
+\item 
+ $
+		P\models{\openrule
+			{
+				\beta_j^{2j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
+				{\Pred^2}',  
+				{\Post^2}'}
+			{\ostate{s_l^{2l\in L\setminus L_Q}} \OTarrow {\alpha}
+				\ostate{s_l'^{\,2l\in L\setminus L_Q}}}
+		}%\]
+	\,\text{and~~}
+		%\[
+		Q\models{\openrule
+			{
+				\beta_j^{2j\in J\cap\Holes(Q)}, {\Pred^2}'',  
+				\Post\,''}
+			{\ostate{s_l^{2l\in L_Q}} \OTarrow {\alpha^2_Q}
+				\ostate{s_l'^{\,2l\in L_Q}}}
+		}%\]
+		$
+		and  $\Pred^2 \iff {\Pred^2}'
+		\land {\Pred^2}''\land \alpha^2_Q=\beta^2_{j_0}$, $\Post^2={\Post^2}'\uplus 
+		{\Post^2}''$ where ${\Post^2}''$ is the restriction of $\Post^2$ over variables of $\Leaves(Q)$.
+\end{enumerate}
+By Lemma \ref{lem-rel-OT-WOT} we can conclude that we have:
+
+\begin{mathpar}
+		P\models{\openrule
+			{
+				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
+				\Pred\,',  
+				\Post\,'}
+			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
+				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
+		}%\]
+\end{mathpar}
+
+Where
+
+\TODO{j'explicite Pred', Post', ect... Mais je ne sais pas trop pour Q???}
 

### 2018-11-16 2016-Weak-FH-Bisim/WeakBisim.tex
reset to commit of 14/11 at 15:09

--- 2018-11-14 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 \\
-		\text{and~~}  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) \qquad
+		\text{and~~}  \bigcup_{\begin{array}{l}
+p\in[0..n]
+\end{array}} J_{p} = J\cap\Holes(Q) \qquad
  \text{and\qquad} \forall j\in J_p,\,\gamma_j= \mybigdotcup_{p=0}^n \gamma_{p j} \\
@@
 \end{lemma}
-\LUDO{A V2 by Ludo}
-
-\begin{proof} Suppose we have: 
+\LUDO{A V2 by Ludo} \TODO{We will check notation  $\alpha_p=...$}
+
+\begin{proof}
+By lemma \ref{lem-rel-OT-WOT} we have: 
 \begin{mathpar}
@@
 \end{mathpar}
-By lemma \ref{lem-rel-OT-WOT} this implies we have: \\			
-$ \forall i \in [0\ldots n]	\,		
+implies 	\\			
+$			
 	P[Q]_{j_0}	\models		
-\openrule
+\Big(\forall i \in [0\ldots n].\openrule
     {
        \set{\gamma^1_i},\Pred^1_i,\Post^1_i   }
-         {\ostate{s^1_i} \OTarrow {\tau} \ostate{s^1_{i+1}}}$
-~and~ $\forall i \in [0\ldots m] \, P[Q]_{j_0}	\models \openrule
-         {
-           \set{\gamma^3_i},\Pred\,^3_i, \Post_i^3   }
-         {\ostate{s^3_i} \OTarrow {\tau} \ostate{s^3_{i+1}}}
-$\\
-and $ P[Q]_{j_0}	\models \openrule
+         {\ostate{s^1_i} \OTarrow {\tau} \ostate{s^1_{i+1}}}\, \wedge\,
+\openrule
          {
@@
          {\ostate{s^2} \OTarrow {\alpha} \ostate{s'^2}}
-$ where\\
+\,\wedge\,
+\forall i \in [0\ldots m].\openrule
+         {
+           \set{\gamma^3_i},\Pred\,^3_i, \Post^3   }
+         {\ostate{s^3_i} \OTarrow {\tau} \ostate{s^3_{i+1}}}
+\Big) 
 $
-s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
-\displaystyle{\gamma_j^{j\in J_1}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i}}}
-\\
-\Pred_{OT}=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\bigotimes_{i=0}^{n}\subst{\Post_i^1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\bigotimes_{i=0}^{n}\subst{\Post^1_i}\\
-\Post_{OT}=\biguplus_{i=0}^{m}(\Post_i^3\subst{\Post^2})\bigotimes_{i=0}^{n}\subst{\Post^1_i}
-$
+
+such that...\\
 

### 2018-11-21 2018-Arch-pNets/arch-pNets.tex
work on substitution lemmas
Eric: figure 4 = Timer open automaton

@@
 
+%	\noindent
+%\begin{mathpar}
+%    \mprset {vskip=1ex}
+%\inferrule
+%    {
+%\Leaves(\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in 
+%    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
+%k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{g} 
+%\\
+%\\     	
+%	\forall m\!\!\in\!\! I_1. {\pNet_m 
+%	\models\openrule
+%    	{
+%    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
+%    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
+%    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
+%  \qquad
+%\forall m\!\!\in\!\! I_2.		{ \pNet_m 
+%    	 \models
+%    	\openrule
+%    	{\emptyset, \Pred_m, \Post_m}
+%    	{\ostate{s_m} \OTarrow {\alpha_m}
+%    		\ostate{s_m'}} }\\\\
+%     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
+%    	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
+%    	\Pred_{\symb{sv}}(SV_k,\alpha_m^{m\in (I_1\uplus I_2)},\beta_j^{j\in J},\alpha)\\ 
+%    		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
+%    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
+%    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
+%    }
+%    {\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
+%    	\models
+%    	{\openrule
+%    		{
+%    		{\beta_j}^{j\in J^\prime}, \Pred, \uplus_{m\in I_1\uplus I_2} 
+%    		\Post_m}
+%    		{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
+%    			\ostate{(s_i^\prime)^{i\in L}}}
+%    	}
+%    }
+%\end{mathpar}  
 	\noindent
 \begin{mathpar}
-    \mprset {vskip=1ex}
+    \mprset {vskip=.8ex}
 \inferrule
     {
-\Leaves(\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in 
+\Leaves(\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in 
     	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
-k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{g} 
+k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
 \\
@@
      J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
-    	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
-    	\Pred_{\symb{sv}}(SV_k,\alpha_m^{m\in (I_1\uplus I_2)},\beta_j^{j\in J},\alpha)\\ 
-    		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
-    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
+    	\Pred = \bigwedge_{m\in I_1\uplus I_2}\!\! \Pred_m \land
+    	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2},\beta_j^{j\in J},\alpha)\\ 
+    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
     \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
     }
-    {\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
+    {\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
     	\models
@@
 
-\Fig{enc:nopri} shows the encoding of the Failure Monitor
+\Fig{fig:FailureTimer:pNet} shows the encoding of the Failure Monitor
 architecture, including the encodings of the two coordinators, \ie
@@
   \includegraphics[width=\columnwidth]{FailureTimerPNET-v4}
-  \caption{The pNET encoding the Failure Monitor architecture (without the priority model)}
+  \caption{The open pNET encoding the Failure Monitor architecture (\fig{schema:ArchFailure:BIP}) without the priority model}
   \label{fig:FailureTimer:pNet}
@@
   \centering
-  \includegraphics[width=\columnwidth]{FailureTimerZonePNET}
-  \caption{The pNET encoding the Failure Monitor architecture}
+  \includegraphics[width=\columnwidth]{TimerOpenAut}
+  \caption{The open Automaton of the Failure Monitor Architecture}
   \label{schema:ArchFailure:BIP}
 \end{figure}
+
+12 open transitions... Comments on the predicates ???
+
+Should list some temporal logic properties....
 
@@
   |[p]| & = p\,,
-  & |x_1 + x_2| & = |x_1| + |x_2|\,,
+  & |x_1 + x_2| & = |x_1| + |x_2|\,,x
   & \left|\prod_{i=1}^n [x_i]\,\right| & = \prod_{i=1}^n |x_k|\,,

### 2018-11-21 2018-Arch-pNets/arch-pNets.tex
pnets notations and properties

@@
 
-\noteLH{a pred is a g a post is a e}
+\noteLH{a pred is a g a post is a u (modified macros!)}
+\renewcommand{\Pred}{g}
+\renewcommand{\Post}{u}
 The semantics of open pNets will be defined  as an open automaton. An open
@@
 \begin{multline}
-\Pred_{\symb{sv}}(\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
+\Predsv(\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
 {\alpha'} {g}, \alpha_i^{i\in I}, \beta_j^{j\in J}, \alpha)\Leftrightarrow \\
@@
 
+\todoLHin{add a paragraph about pnets properties and usage, here are a few points (to be completed and written up properly depending on what we need}
+
+- pnets as a model for gcm components (behaviour, distributed systems, verification)
+
+- used for finite model checking (with finite domains for parameters)
+
+- smt framework for reasoning on infinite models
+
+- a theory of pnets: composition properties , stong (and weak) bisim
+	** extract a few useful composition theorems? **
+
 %OLD	\begin{description}
@@
 
-\Fig{fig:FailureTimer:pNet} shows the encoding of the Failure Monitor
+\Fig{enc:nopri} shows the encoding of the Failure Monitor
 architecture, including the encodings of the two coordinators, \ie
@@
   \includegraphics[width=\columnwidth]{FailureTimerPNET-v4}
-  \caption{The open pNET encoding the Failure Monitor architecture (\fig{schema:ArchFailure:BIP}) without the priority model}
+  \caption{The pNET encoding the Failure Monitor architecture (without the priority model)}
   \label{fig:FailureTimer:pNet}
@@
   \centering
-  \includegraphics[width=\columnwidth]{TimerOpenAut}
-  \caption{The open Automaton of the Failure Monitor Architecture}
+  \includegraphics[width=\columnwidth]{FailureTimerZonePNET}
+  \caption{The pNET encoding the Failure Monitor architecture}
   \label{schema:ArchFailure:BIP}
 \end{figure}
-
-12 open transitions... Comments on the predicates ???
-
-Should list some temporal logic properties....
 

### 2018-11-22 2016-Weak-FH-Bisim/WeakBisim.tex
proof lemma 5

@@
 \end{lemma}
-\LUDO{A V2 by Ludo} \TODO{We will check notation  $\alpha_p=...$}
-
-\begin{proof}
-By lemma \ref{lem-rel-OT-WOT} we have: 
+\LUDO{A V2 by Ludo}
+
+\newpage
+\begin{proof} Suppose we have: 
 \begin{mathpar}
@@
 \end{mathpar}
-implies 	\\			
+By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
+$ \forall i \in [0\ldots n]	\,		
+	P[Q]_{j_0}	\models		
+\openrule
+    {
+       \set{(\beta^1_i)},\Pred^1_i,\Post^1_i   }
+         {\ostate{s^1_i} \OTarrow {\tau} \ostate{s^1_{i+1}}}$
+~and~ $\forall i \in [0\ldots m] \, P[Q]_{j_0}	\models \openrule
+         {
+           \set{(\beta^3_i)},\Pred\,^3_i, \Post_i^3   }
+         {\ostate{s^3_i} \OTarrow {\tau} \ostate{s^3_{i+1}}}
+$\\
+and $ P[Q]_{j_0}	\models \openrule
+         {
+           \set{\beta^2},\Pred\,^2,\Post^2 }
+         {\ostate{s^2} \OTarrow {\alpha} \ostate{s'^2}}
+$ where\\
 $
-	P[Q]_{j_0}	\models		
-\Big(\forall i \in [0\ldots n].\openrule
-    {
-       \set{\gamma^1_i},\Pred^1_i,\Post^1_i   }
-         {\ostate{s^1_i} \OTarrow {\tau} \ostate{s^1_{i+1}}}\, \wedge\,
-\openrule
-         {
-           \set{\gamma^2},\Pred\,^2,\Post^2 }
-         {\ostate{s^2} \OTarrow {\alpha} \ostate{s'^2}}
-\,\wedge\,
-\forall i \in [0\ldots m].\openrule
-         {
-           \set{\gamma^3_i},\Pred\,^3_i, \Post^3   }
-         {\ostate{s^3_i} \OTarrow {\tau} \ostate{s^3_{i+1}}}
-\Big) 
+s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
+\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i}}}
+\\
+\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\bigotimes_{i=0}^{n}\subst{\Post_i^1}\land (\bigwedge_{i=0}^m\Pred\,^3_i\subst{\Post^2})\bigotimes_{i=0}^{n}\subst{\Post^1_i}\\
+\Post=\biguplus_{i=0}^{m}(\Post^3_i\subst{\Post^2})\bigotimes_{i=0}^{n}\subst{\Post^1_i}
 $
 
-such that...\\
-
-On other hand by Theorem \ref{thm-composability} we have:
-
-\TODO{La preuve page 27 est difficile a suivre...}
+We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$:
+\begin{enumerate}
+\item For  $\symb{OT}$ in the form: 
+$P[Q]_{j_0}	\models		\openrule
+    {
+       \set{\beta}_p,\Pred_p,\Post_p   }
+         {\ostate{s_p} \OTarrow {\tau} \ostate{s^1_{p+1}}}$ \\
+We obtain:\\
+$P\models{\openrule
+			{
+				(\beta_{p})_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
+				{\Pred_p}\!\!',  
+				{\Post_p}\!\!'}
+			{\ostate{(s_{p})_l^{l\in L\setminus L_Q}} \OTarrow {\tau}
+				\ostate{({s}_{p}')_l^{l\in L\setminus L_Q}}}
+		}%\]
+	\,\text{~~and~~}
+		%\[
+		Q\models{\openrule
+			{
+				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {\Pred_p''},  
+				{\Post_p''}}
+			{\ostate{(s_{p})_l^{l\in L_Q}} \OTarrow {\alpha_p}
+				\ostate{({s_{(p+1)}})_l^{l\in L_Q}}}
+		}%\]
+		$\\
+and  $\Pred_p \iff {\Pred_p}\!\!'
+		\land {\Pred_p}\!\!''\land \alpha_p=\beta_{pj_0}$, $\Post_p={\Post_p}\!\!'\uplus 
+		{\Post_p}\!\!''$ where ${\Post_p''}$ is the restriction of $\Post_p$ over variables of $\Leaves(Q)$.
+\item For $\symb{OT}$ in the form: $P[Q]_{j_0}	\models \openrule
+         {
+           \set{\beta},\Pred,\Post }
+         {\ostate{s} \OTarrow {\alpha} \ostate{s'}}$\\
+We obtain:\\
+$
+		P\models{\openrule
+			{
+				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
+				{\Pred}\,',  
+				{\Post}\,'}
+			{\ostate{s_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
+				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
+		}%\]
+	\,\text{~~and~~}
+		%\[
+		Q\models{\openrule
+			{
+				\beta_j^{j\in J\cap\Holes(Q)}, {\Pred}\,'',  
+				{\Post}\,''}
+			{\ostate{s_l^{l\in L_Q}} \OTarrow {\alpha'}
+				\ostate{s_l'^{\,l\in L_Q}}}
+		}%\]
+		$
+		and  $\Pred \iff {\Pred}\,'
+		\land {\Pred}\,''\land \alpha'=\beta_{j_0}$, $\Post={\Post}\,'\uplus 
+		{\Post}\,''$ where ${\Post}\,''$ is the restriction of $\Post$ over variables of $\Leaves(Q)$.
+
+\end{enumerate}
+By using  Lemma \ref{lem-rel-OT-WOT} we can conclude that we have:
+
+\begin{mathpar}
+		P\models{\openrule
+			{
+				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
+				\Pred\,',  
+				\Post\,'}
+			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
+				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
+		}%\]
+\end{mathpar}
+
+Where \TODO{I will add the rest}
+
+Considering the set of $\symb{OT}_p$ of $Q$ such that $p \in [0\ldots m+n+1]$, at each time a single open transition moves.   So we have for each open transition:
+
+\begin{mathpar}
+Q\models{\openrule
+			{
+				\beta_{pj}^{j\in J\cap\Holes(Q)}, {\Pred_p},  
+				{\Post_p}}
+			{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
+				\ostate{s_{(p+1)l}^{l\in L_Q}}}
+		}%\]
+
+\end{mathpar}
+
+By definition \ref{def:buildweakOT} we can conclude that we have for all $p\in[0\ldots n+m]$:
+
+\begin{mathpar}
+Q\models{\openrule
+			{
+				{\gamma_{pj}^{j\in J_p}}, {\Pred_p},  
+				{\Post_p}'}
+			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha_{p}}
+				\ostate{s_{(p+1)l}^{l\in L_Q}}}
+		}%\]
+
+\end{mathpar}
+
+Where $J_p = J\cap\Holes(Q)$, ???? $\gamma_{pj}=\vis{\beta_{pj}}$,\\  $\Pred \iff \Pred\,'
+		\land \displaystyle{\bigvee_{p=0}^n}(\alpha_p= \beta_{pj_0}\land \Pred_p), \text{and~}
+\Post=\Post\,'\uplus\biguplus_{p=0}^n
+		\Post_p$
 
 \end{proof}
+---------------------------------------------------------
+
 \begin{lemma}[WOT decomposition]\label{lem-wot-decompose} 

### 2018-11-22 2016-Weak-FH-Bisim/WeakBisim.tex
after skype

@@
 \TODO{Ludo: in the next 2 theorems I have a doubt about the biguplus of post p : not sure they should be disjoint, but else we need to do a complex composition  of posts}
-\begin{lemma}[Weak OT decomposition]\label{lem-decompose} 
+\begin{lemma}[Weak OT decomposition]\label{lem-decomposeWOT} 
 	Let $\Leaves(Q)=pLTS_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
@@
 \end{proof}
----------------------------------------------------------
-
-\begin{lemma}[WOT decomposition]\label{lem-wot-decompose} 
-	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
-	lemma imply that $Q$ is 
-	not a \pLTS\ but a similar lemma can be proven for a pLTS $Q$}:
-	\[ P[Q]_{j_0}  
-		\models
-		{\openrule
-			{
-				\gamma_j^{j\in J}, \Pred,  
-				\Post}
-			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
-				\ostate{s_i'^{\, i\in L}}}
-		}
-	\]
-		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e.
-$Q$ takes part in the reduction\footnote{Note that necessarily $\alpha_Q\neq \tau$ as soon as silent actions are not observable Definition~\ref{def:Non-ObsTau}.}.
-		 Then there exist $\alpha_Q$, $\Pred\,'$, $\Pred\,''$, 
-		$\Post\,'$, $\Post\,''$ s.t.:\\[-2ex]
-		%\[
-		\begin{mathpar}
-		P\models{\openrule
-			{
-				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
-				\Pred\,',  
-				\Post\,'}
-			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
-				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
-		}%\]
-	\vspace{-2.2ex}\\\text{and~~}
-		%\[
-		Q\models{\openrule
-			{
-				\gamma_j^{j\in J\cap\Holes(Q)}, \Pred\,'',  
-				\Post\,''}
-			{\ostate{s_i^{i\in L_Q}} \OTWeakarrow {\alpha_Q}
-				\ostate{s_i'^{\,i\in L_Q}}}
-		}%\]
-		\end{mathpar}
-		and  $\Pred \iff \Pred\,'
-		\land \Pred\,''\land \gamma_{j_0}=[\alpha_Q]$, $\Post=\Post\,'\uplus 
-		\Post\,''$ where $\Post\,''$ is the restriction of $\Post$ over variables of 
-		$\Leaves(Q)$.
-
-\end{lemma}
-
-\TODO{proof}
 

### 2018-11-29 2016-Weak-FH-Bisim/WeakBisim.tex
lemma 5

@@
 				{\Post_p''}}
-			{\ostate{(s_{p})_l^{l\in L_Q}} \OTarrow {\alpha_p}
-				\ostate{({s_{(p+1)}})_l^{l\in L_Q}}}
+				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
+				\ostate{s_{(p+1)l}^{l\in L_Q}}}
 				}%\]
@@
 				\Post\,'}
-			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
-				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
+			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
+				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
 		}%\]
@@
 
-Considering the set of $\symb{OT}_p$ of $Q$ such that $p \in [0\ldots m+n+1]$, at each time a single open transition moves.   So we have for each open transition:
+Considering the set of $\symb{OT}_p$ of $Q$ such that $p \in S$ and $S \subseteq [0\ldots m+n+1]$, at each time a single open transition moves.   So we have for each open transition:
 
@@
 
-By definition \ref{def:buildweakOT} we can conclude that we have for all $p\in[0\ldots n+m]$:
+By definition \ref{def:buildweakOT} we can conclude that we have for all $p\in S$:
 
@@
 
-Where $J_p = J\cap\Holes(Q)$, ???? $\gamma_{pj}=\vis{\beta_{pj}}$,\\  $\Pred \iff \Pred\,'
+Where\\ $\displaystyle{\bigcup_{p=0}^nJ_{p}} = J\cap\Holes(Q)$, $\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}}$, $\forall l\in L_Q,\, s_{0l}=s_l$, $s_{(n+1)l}=s'_l$  \\
+  $\Pred \iff \Pred\,'
 		\land \displaystyle{\bigvee_{p=0}^n}(\alpha_p= \beta_{pj_0}\land \Pred_p), \text{and~}
 \Post=\Post\,'\uplus\biguplus_{p=0}^n
-		\Post_p$
+		\Post_p \quad$
+
+\TODO{We will discuss quantif.}
 

### 2018-11-29 2018-Arch-pNets/arch-pNets.tex
very small stuff...

@@
 \newcommand{\Simon}{\\\hfill\mdash Simon}
+\newcommand{\Eric}{\\\hfill\mdash Eric}
 
@@
 \newcommand{\todoLHin}[2][inline,color=orange!40]{\todo[#1]{\textbf{To-do Ludo: } {#2}}}
+\newcommand{\todoEM}[2][color=green!40, size=\tiny]{\todo[#1]{\textbf{To-do Eric:} {#2}}}
 
@@
   \and
+    Universit\'e C\^ote d'Azur, Inria, CNRS, I3S, 06902 Sophia-Antipolis, France\\
+  \email{eric.madelaine@inria.fr}
 }
@@
 
-\noteLHin{I believe we should simplify this paragraph about param actions}
+\noteLHin{I believe we should simplify this paragraph about param actions
+
+  I agree with this, but also we may look at what is useful here, and what is only used later in pLTS/pNet definitions. 
+\Eric}
 The pNet model in \secn{pNets} relies on a notion of parameterised actions, that are
@@
 and $\variables$ a set of \emph{variables}. Within $\Talg$, we distinguish a set of
-\emph{data expressions} $\exprs{\variables}$ \replaceSB{, including}{and} a set of \emph{Boolean
+\emph{data expressions} $\exprs{\variables}$ and a set of \emph{Boolean
 expressions} \todoLH{$\mathcal{B} \to g$}
@@
 $t\in\Talg$, and $iv(t)$ returns its input variables.
-Action algebras can \replaceSB{encode naturally }{naturally encode }usual point-to-point message passing calculi (using 
+Action algebras can naturally encode usual point-to-point message passing calculi (using 
 $a(?x_1,\dots,?x_n)$ for inputs, $a(v_1,\dots,v_n)$ for outputs), but it also allows
@@
   \label{OT:enable-composed}
-  The \texttt{EnableCompL} pNet of Fig. \ref{schema:enable-composed} has 2 controllers 
+  \todoEM{remplacer cette OT par une du Timer, qui aurait tous les elements presents...}
+  The \texttt{Failure TimerMonitor} pNet of \Fig{FailureTimer:pNet} has 2 controllers 
   and 2 holes.
@@
 
-\Fig{fig:FailureTimer:pNet} shows the encoding of the Failure Monitor
+\Fig{FailureTimer:pNet} shows the encoding of the Failure Monitor
 architecture, including the encodings of the two coordinators, \ie
@@
 
-\begin{figure*}[t]
-  \fbox{%
-  \includegraphics[width=\textwidth]{BIPspec-ArchFailureTimerMax-v4-no-pri}}
-  \caption{Encoding of the Failure Monitor architecture
-    (\fig{schema:ArchFailure:BIP}) as an open pNet (without the
-    priority model) \hl{\bf (Error in the picture: First two positions in the synchronisation vectors must be transposed)}}
-  \label{fig:enc:nopri}
-\end{figure*}
+%% \begin{figure*}[t]
+%%   \fbox{%
+%%   \includegraphics[width=\textwidth]{BIPspec-ArchFailureTimerMax-v4-no-pri}}
+%%   \caption{Encoding of the Failure Monitor architecture
+%%     (\fig{schema:ArchFailure:BIP}) as an open pNet (without the
+%%     priority model) \hl{\bf (Error in the picture: First two positions in the synchronisation vectors must be transposed)}}
+%%   \label{fig:enc:nopri}
+%% \end{figure*}
 
@@
 allowed interactions, depending on its hierarchical structure and the
-use of syncrhons and trigger.  \noteSB{Move this to
+use of synchrons and triggers.  \noteSB{Move this to
   \secn{components}?}For instance, the connector {\NameTimer.\PortTick

### 2018-11-30 2018-Arch-pNets/arch-pNets.tex
listing brut du calcul des OT

@@
 
+\subsection{Full results of the use-case}
+\label{secn:full-results}
+
+\subsubsection{Output of the open-automaton construction}
+The standard pretty-print of OTs by the tool include the transitions of the pLTSs (controllers).
+This is not a full ``proof-carrying code'', but it allows for a better understanding of the construction of each OT.
+
+\begin{verbatim}
+INFO  BIPArchFailureTimerMax_LTF3 - Total: 12 OTs
+INFO  BIPArchFailureTimerMax_LTF3 -
+        {t0---init-->t1, s0---init-->s1},   {},   
+        [((init=:ra:117:1))/\((:ra:117:1=init))/\((init=:ra:118:1))/\((:ra:118:1=ini
+t))/\((alpha4=:ra:1:5))],   {t := 0, z := TopInt, zone := minZone,maxZone}
+    OT ------------------------------------------------------------
+        <t0_s0>-----:ra:1:5----><t1_s1>
+
+INFO  BIPArchFailureTimerMax_LTF3 -
+     {t1---tick(z, t, z1)-->t1, s1---fail(zone, false)-->s1},   {---:hb_B:13:1-->},   
+     [((t<GET_MAX z))/\((tick(z, t, z1)=:ra:11:1))/\((:ra:11:1=tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
+/\((fail(zone, false)=:ra:12:1))/\((:ra:12:1=fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))/\
+((:hb_B:13:1=fail(b0:sva_SV0:1:1)))/\((b1:sva_SV0:1:1->b0:sva_SV0:1:1)/\
+(z1:sva_SV0:1:1=z:sva_SV0:1:1/\(((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt)))+t:sva_SV0:1:1)))/\((alpha0=:ra:1:1))],
+   {t := (t+1), z := z1}
+    OT ------------------------------------------------------------
+        <t1_s1>-----:ra:1:1----><t1_s1>
+
+INFO  BIPArchFailureTimerMax_LTF3 -
+        {t1---tick(z, t, z1)-->t1, s1---fail(zone, true)-->s2},   {---:hb_B:13:1-->},   [((t<GET_MAX z))/\((tick(z, t, z1)=:ra
+:11:1))/\((:ra:11:1=tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))/\((fail(zone, true)=:ra:12:1))/\((:ra:12:1=fail
+(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))/\((:hb_B:13:1=fail(b0:sva_SV0:1:1)))/\((b1:sva_SV0:1:1->b0:sva_SV0:1:1)/\(z1:sva_SV
+0:1:1=z:sva_SV0:1:1/\(((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt)))+t:sva_SV0:1:1)))/\((alpha0=:ra:1:1))],   {t := (t+1
+), z := z1}
+    OT ------------------------------------------------------------
+        <t1_s1>-----:ra:1:1----><t1_s2>
+
+INFO  BIPArchFailureTimerMax_LTF3 -
+        {t1---cancel(false)-->t1, s1---resume(false)-->s1},   {---:hb_B:17:3-->},   [((cancel(false)=:ra:15:1))/\((:ra:15:1=ca
+ncel(b1:sva_SV1:1:2)))/\((resume(false)=:ra:16:1))/\((:ra:16:1=resume(b2:sva_SV1:1:2)))/\((:hb_B:17:3=resume))/\((b1:sva
+_SV1:1:2=b2:sva_SV1:1:2))/\((alpha1=:ra:1:2))],   {}
+    OT ------------------------------------------------------------
+        <t1_s1>-----:ra:1:2----><t1_s1>
+
+INFO  BIPArchFailureTimerMax_LTF3 -
+        {t1---timeout-->t1, s1---timeout-->s1},   {---:hb_E:112:6-->},   [(t in z)/\((timeout=:ra:19:1))/\((:ra:19:1=timeout))
+/\((timeout=:ra:110:1))/\((:ra:110:1=timeout))/\((:hb_E:112:6=ask))/\((alpha2=:ra:1:3))],   {t := (t+1)}
+    OT ------------------------------------------------------------
+        <t1_s1>-----:ra:1:3----><t1_s1>
+
+INFO  BIPArchFailureTimerMax_LTF3 -
+        {t1---tick(z, t, z1)-->t1, s2---fail(zone, false)-->s2},   {---:hb_B:13:1-->},   [((t<GET_MAX z))/\((tick(z, t, z1)=:r
+a:11:1))/\((:ra:11:1=tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))/\((fail(zone, false)=:ra:12:1))/\((:ra:12:1=fa
+il(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))/\((:hb_B:13:1=fail(b0:sva_SV0:1:1)))/\((b1:sva_SV0:1:1->b0:sva_SV0:1:1)/\(z1:sva_
+SV0:1:1=z:sva_SV0:1:1/\(((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt)))+t:sva_SV0:1:1)))/\((alpha0=:ra:1:1))],   {t := (t
++1), z := z1}
+    OT ------------------------------------------------------------
+        <t1_s2>-----:ra:1:1----><t1_s2>
+
+INFO  BIPArchFailureTimerMax_LTF3 -
+        {t1---cancel(false)-->t1, s2---resume(false)-->s2},   {---:hb_B:17:3-->},   [((cancel(false)=:ra:15:1))/\((:ra:15:1=ca
+ncel(b1:sva_SV1:1:2)))/\((resume(false)=:ra:16:1))/\((:ra:16:1=resume(b2:sva_SV1:1:2)))/\((:hb_B:17:3=resume))/\((b1:sva
+_SV1:1:2=b2:sva_SV1:1:2))/\((alpha1=:ra:1:2))],   {}
+    OT ------------------------------------------------------------
+        <t1_s2>-----:ra:1:2----><t1_s2>
+
+INFO  BIPArchFailureTimerMax_LTF3 -
+        {t1---cancel(true)-->t1, s2---resume(true)-->s1},   {---:hb_B:17:3-->},   [((cancel(true)=:ra:15:1))/\((:ra:15:1=cance
+l(b1:sva_SV1:1:2)))/\((resume(true)=:ra:16:1))/\((:ra:16:1=resume(b2:sva_SV1:1:2)))/\((:hb_B:17:3=resume))/\((b1:sva_SV1
+:1:2=b2:sva_SV1:1:2))/\((alpha1=:ra:1:2))],   {t := 0, z := TopInt}
+    OT ------------------------------------------------------------
+        <t1_s2>-----:ra:1:2----><t1_s1>
+
+INFO  BIPArchFailureTimerMax_LTF3 -
+        {t1---timeout-->t1, s2---timeout-->s3},   {---:hb_E:112:6-->},   [(t in z)/\((timeout=:ra:19:1))/\((:ra:19:1=timeout))
+/\((timeout=:ra:110:1))/\((:ra:110:1=timeout))/\((:hb_E:112:6=ask))/\((alpha2=:ra:1:3))],   {t := (t+1)}
+    OT ------------------------------------------------------------
+        <t1_s2>-----:ra:1:3----><t1_s3>
+
+INFO  BIPArchFailureTimerMax_LTF3 -
+        {t1---tick(z, t, z1)-->t1, s3---fail(zone, false)-->s3},   {---:hb_B:13:1-->},   [((t<GET_MAX z))/\((tick(z, t, z1)=:r
+a:11:1))/\((:ra:11:1=tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))/\((fail(zone, false)=:ra:12:1))/\((:ra:12:1=fa
+il(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))/\((:hb_B:13:1=fail(b0:sva_SV0:1:1)))/\((b1:sva_SV0:1:1->b0:sva_SV0:1:1)/\(z1:sva_
+SV0:1:1=z:sva_SV0:1:1/\(((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt)))+t:sva_SV0:1:1)))/\((alpha0=:ra:1:1))],   {t := (t
++1), z := z1}
+    OT ------------------------------------------------------------
+        <t1_s3>-----:ra:1:1----><t1_s3>
+
+INFO  BIPArchFailureTimerMax_LTF3 -
+        {t1---cancel(false)-->t1, s3---resume(false)-->s3},   {---:hb_B:17:3-->},   [((cancel(false)=:ra:15:1))/\((:ra:15:1=ca
+ncel(b1:sva_SV1:1:2)))/\((resume(false)=:ra:16:1))/\((:ra:16:1=resume(b2:sva_SV1:1:2)))/\((:hb_B:17:3=resume))/\((b1:sva
+_SV1:1:2=b2:sva_SV1:1:2))/\((alpha1=:ra:1:2))],   {}
+    OT ------------------------------------------------------------
+        <t1_s3>-----:ra:1:2----><t1_s3>
+
+INFO  BIPArchFailureTimerMax_LTF3 -
+        {s3---reset-->s1},   {---:hb_E:116:8-->},   [((reset=:ra:114:1))/\((:ra:114:1=reset))/\((:hb_E:116:8=reset))/\((alpha3
+=:ra:1:4))],   {}
+    OT ------------------------------------------------------------
+        <t1_s3>-----:ra:1:4----><t1_s1>
+
+INFO  BIPArchFailureTimerMax_LTF3 - Total: 12 SATISFIABLE OTs
+INFO  BIPArchFailureTimerMax_LTF3 -        235 UNSATISFIABLE OTs
+INFO  BIPArchFailureTimerMax_LTF3 - Total Time: 1293 ms
+FailureTimerArchi
+--------------------
+SV0 SVs: <tick(z, t, z1), fail(zone, b1), fail(b0), _>-->alpha0, ((b1->b0)/\(z1=z/\(((b1?(zone)TopInt)))+t)))
+SV1 SVs: <cancel(b1), resume(b2), resume, _>-->alpha1, (b1=b2)
+SV2 SVs: <timeout, timeout, _, ask>-->alpha2
+SV3 SVs: <_, reset, _, reset>-->alpha3
+SV4 SVs: <init, init, _, _>-->alpha4
+pLTS: Timer
+- Transition: t0---init-->t1, { t := 0 z := TopInt}
+- Transition: t1---tick(z, t, z1)-->t1, [(t<GET_MAX z)], { t := (t+1) z := z1}
+- Transition: t1---cancel(false)-->t1, {}
+- Transition: t1---cancel(true)-->t1, { t := 0 z := TopInt}
+- Transition: t1---timeout-->t1, [t in z], { t := (t+1)}
+- Variable: t, State: t1, Value(s) = 0,0,(t+1),
+- Variable: z, State: t1, Value(s) = TopInt,z1,
+pLTS: Failure
+- Transition: s0---init-->s1, { zone := minZone,maxZone}
+- Transition: s1---timeout-->s1, {}
+- Transition: s1---resume(false)-->s1, {}
+- Transition: s1---fail(zone, false)-->s1, {}
+- Transition: s1---fail(zone, true)-->s2, {}
+- Transition: s2---fail(zone, false)-->s2, {}
+- Transition: s2---resume(false)-->s2, {}
+- Transition: s2---resume(true)-->s1, {}
+- Transition: s2---timeout-->s3, {}
+- Transition: s3---fail(zone, false)-->s3, {}
+- Transition: s3---resume(false)-->s3, {}
+- Transition: s3---reset-->s1, {}
+- Variable: zone, State: s1, Value(s) = minZone,maxZone,
+Holes: B
+Holes: E
+\end{verbatim}
+
 \end{document}

### 2018-11-30 2018-Arch-pNets/arch-pNets.tex
mise en forme verbatim OTs

--- 2018-11-29 2018-Arch-pNets/arch-pNets.tex
@@
   \label{OT:enable-composed}
-  \todoEM{remplacer cette OT par une du Timer, qui aurait tous les elements presents...}
+  \todoEM{Commenter...}
   The \texttt{Failure TimerMonitor} pNet of \Fig{FailureTimer:pNet} has 2 controllers 
-  and 2 holes.
-One of its possible open-transition is\footnote{Note the underlined action notation that we use to represent synchronised actions, i.e.
+  and 2 holes. Two of its possible open-transitions are:
+
+%%   \footnote{Note the underlined action notation that we use to represent synchronised actions, i.e.
 actions that are the result of a synchronisation and that we declare as \emph{non-observable}.
 Those actions are only used for monitoring purposes and statement of properties but cannot be synchronised again in a synchronisation vector.
-This allows us to define a weak bisimilarity equivalence with p=compositional properties.}:
-\noteLH{underline notation might be a bit too much for this paper : see at the end if we remove it or not (will we use it?)}
+This allows us to define a weak bisimilarity equivalence with p=compositional properties.}
+%%   : 
+%% \noteLH{underline notation might be a bit too much for this paper : see at the end if we remove it or not (will we use it?)}
 
  \smallskip
- $  OT_2  = \openrule{ 
-							(P\mapsto \delta(x4), Q\mapsto accept(x4))               
-%                            \xrightarrow{\delta(x4)}_P ~~
-%                            \xrightarrow{accept(x4)}_Q 
-                      }
-  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
-    {A1_0 \OTarrow{\underline{\delta(x4)}} A1_1}
+$  OT_1  = \openrule
+{\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
+{\ostate{00} \OTarrow{\underline{\alpha_4}} \ostate{11}}
 $
+\medskip
+
+  $  OT_3  = \openrule
+  {\{B\mapsto fail(b0)\},\\
+    t<GetMax(z) \land b1=true \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),
+    \{z:=z1\} }
+  {\ostate{11} \OTarrow{\underline{\alpha_0}} \ostate{12}}
+  $
+
 \end{example}
@@
 
+\subsection{Full results of the use-case}
+\label{secn:full-results}
+
+\subsubsection{Output of the open-automaton construction}
+The standard pretty-print of OTs by the tool include the transitions
+of the pLTSs (controllers). This is not a full ``proof-carrying
+code'', but it allows for a better understanding of the construction
+of each OT.
+
+We first show the pNet input, then the twelve generated OTs in their
+verbatim form.
+
+\small\begin{verbatim}
+FailureTimerArchi
+--------------------
+SV0 SVs: <tick(z, t, z1), fail(zone, b1), fail(b0), _>-->alpha0,
+                          [((b1->b0)/\(z1=z/\(((b1?(zone)TopInt)))+t)))]
+SV1 SVs: <cancel(b1), resume(b2), resume, _>-->alpha1, (b1=b2)
+SV2 SVs: <timeout, timeout, _, ask>-->alpha2
+SV3 SVs: <_, reset, _, reset>-->alpha3
+SV4 SVs: <init, init, _, _>-->alpha4
+pLTS: Timer
+- Transition: t0---init-->t1, { t := 0 z := TopInt}
+- Transition: t1---tick(z, t, z1)-->t1, [(t<GET_MAX z)], { t := (t+1) z := z1}
+- Transition: t1---cancel(false)-->t1, {}
+- Transition: t1---cancel(true)-->t1, { t := 0 z := TopInt}
+- Transition: t1---timeout-->t1, [t in z], { t := (t+1)}
+- Variable: t, State: t1, Value(s) = 0,0,(t+1),
+- Variable: z, State: t1, Value(s) = TopInt,z1,
+pLTS: Failure
+- Transition: s0---init-->s1, { zone := minZone,maxZone}
+- Transition: s1---timeout-->s1, {}
+- Transition: s1---resume(false)-->s1, {}
+- Transition: s1---fail(zone, false)-->s1, {}
+- Transition: s1---fail(zone, true)-->s2, {}
+- Transition: s2---fail(zone, false)-->s2, {}
+- Transition: s2---resume(false)-->s2, {}
+- Transition: s2---resume(true)-->s1, {}
+- Transition: s2---timeout-->s3, {}
+- Transition: s3---fail(zone, false)-->s3, {}
+- Transition: s3---resume(false)-->s3, {}
+- Transition: s3---reset-->s1, {}
+- Variable: zone, State: s1, Value(s) = minZone,maxZone,
+Holes: B
+Holes: E
+
+-------------------------------------------
+INFO  BIPArchFailureTimerMax_LTF3 - Total: 12 OTs
+INFO  BIPArchFailureTimerMax_LTF3 -
+        {t0---init-->t1, s0---init-->s1},   {},   
+        [((init=:ra:117:1))/\((:ra:117:1=init))/\((init=:ra:118:1))/\((:ra:118:1=init))
+          /\((alpha4=:ra:1:5))],   {t := 0, z := TopInt, zone := minZone,maxZone}
+    OT1 ------------------------------------------------------------
+        <t0_s0>-----:ra:1:5----><t1_s1>
+
+INFO  BIPArchFailureTimerMax_LTF3 -
+     {t1---tick(z, t, z1)-->t1, s1---fail(zone, false)-->s1},   {---:hb_B:13:1-->},   
+     [((t<GET_MAX z))/\((tick(z, t, z1)=:ra:11:1))
+       /\((:ra:11:1=tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
+       /\((fail(zone, false)=:ra:12:1))
+       /\((:ra:12:1=fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))/\
+       ((:hb_B:13:1=fail(b0:sva_SV0:1:1)))/\((b1:sva_SV0:1:1->b0:sva_SV0:1:1)/\
+       (z1:sva_SV0:1:1=z:sva_SV0:1:1/\(((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt)))+t:sva_SV0:1:1)))
+       /\((alpha0=:ra:1:1))],
+   {t := (t+1), z := z1}
+    OT2 ------------------------------------------------------------
+        <t1_s1>-----:ra:1:1----><t1_s1>
+
+INFO  BIPArchFailureTimerMax_LTF3 -
+   {t1---tick(z, t, z1)-->t1, s1---fail(zone, true)-->s2},   {---:hb_B:13:1-->},
+   [((t<GET_MAX z))/\((tick(z, t, z1)=:ra:11:1))
+     /\((:ra:11:1=tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
+     /\((fail(zone, true)=:ra:12:1))/\((:ra:12:1=fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
+     /\((:hb_B:13:1=fail(b0:sva_SV0:1:1)))/\((b1:sva_SV0:1:1->b0:sva_SV0:1:1)
+     /\(z1:sva_SV0:1:1=z:sva_SV0:1:1/\(((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt)))+t:sva_SV0:1:1)))
+     /\((alpha0=:ra:1:1))],   {t := (t+1), z := z1}
+    OT3 ------------------------------------------------------------
+        <t1_s1>-----:ra:1:1----><t1_s2>
+
+INFO  BIPArchFailureTimerMax_LTF3 -
+   {t1---cancel(false)-->t1, s1---resume(false)-->s1},   {---:hb_B:17:3-->},
+   [((cancel(false)=:ra:15:1))/\((:ra:15:1=cancel(b1:sva_SV1:1:2)))
+     /\((resume(false)=:ra:16:1))/\((:ra:16:1=resume(b2:sva_SV1:1:2)))
+     /\((:hb_B:17:3=resume))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2))/\((alpha1=:ra:1:2))],   {}
+    OT4 ------------------------------------------------------------
+        <t1_s1>-----:ra:1:2----><t1_s1>
+
+INFO  BIPArchFailureTimerMax_LTF3 -
+{t1---timeout-->t1, s1---timeout-->s1},   {---:hb_E:112:6-->},
+[(t in z)/\((timeout=:ra:19:1))/\((:ra:19:1=timeout))
+/\((timeout=:ra:110:1))/\((:ra:110:1=timeout))/\((:hb_E:112:6=ask))/\((alpha2=:ra:1:3))], {t := (t+1)}
+    OT5 ------------------------------------------------------------
+        <t1_s1>-----:ra:1:3----><t1_s1>
+
+INFO  BIPArchFailureTimerMax_LTF3 -
+   {t1---tick(z, t, z1)-->t1, s2---fail(zone, false)-->s2},   {---:hb_B:13:1-->},
+   [((t<GET_MAX z))/\((tick(z, t, z1)=:ra:11:1))
+     /\((:ra:11:1=tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
+     /\((fail(zone, false)=:ra:12:1))/\((:ra:12:1=fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
+     /\((:hb_B:13:1=fail(b0:sva_SV0:1:1)))/\((b1:sva_SV0:1:1->b0:sva_SV0:1:1)
+     /\(z1:sva_SV0:1:1=z:sva_SV0:1:1/\(((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt)))+t:sva_SV0:1:1)))
+     /\((alpha0=:ra:1:1))],   {t := (t+1), z := z1}
+    OT6 ------------------------------------------------------------
+        <t1_s2>-----:ra:1:1----><t1_s2>
+
+INFO  BIPArchFailureTimerMax_LTF3 -
+   {t1---cancel(false)-->t1, s2---resume(false)-->s2},   {---:hb_B:17:3-->},
+   [((cancel(false)=:ra:15:1))/\((:ra:15:1=cancel(b1:sva_SV1:1:2)))
+     /\((resume(false)=:ra:16:1))/\((:ra:16:1=resume(b2:sva_SV1:1:2)))
+     /\((:hb_B:17:3=resume))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2))/\((alpha1=:ra:1:2))],   {}
+    OT7 ------------------------------------------------------------
+        <t1_s2>-----:ra:1:2----><t1_s2>
+
+INFO  BIPArchFailureTimerMax_LTF3 -
+   {t1---cancel(true)-->t1, s2---resume(true)-->s1},   {---:hb_B:17:3-->},
+   [((cancel(true)=:ra:15:1))/\((:ra:15:1=cancel(b1:sva_SV1:1:2)))
+     /\((resume(true)=:ra:16:1))/\((:ra:16:1=resume(b2:sva_SV1:1:2)))
+     /\((:hb_B:17:3=resume))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2))/\((alpha1=:ra:1:2))],
+   {t := 0, z := TopInt}
+    OT8 ------------------------------------------------------------
+        <t1_s2>-----:ra:1:2----><t1_s1>
+
+INFO  BIPArchFailureTimerMax_LTF3 -
+   {t1---timeout-->t1, s2---timeout-->s3},   {---:hb_E:112:6-->},
+   [(t in z)/\((timeout=:ra:19:1))/\((:ra:19:1=timeout))
+     /\((timeout=:ra:110:1))/\((:ra:110:1=timeout))/\((:hb_E:112:6=ask))/\((alpha2=:ra:1:3))],
+   {t := (t+1)}
+    OT9 ------------------------------------------------------------
+        <t1_s2>-----:ra:1:3----><t1_s3>
+
+INFO  BIPArchFailureTimerMax_LTF3 -
+   {t1---tick(z, t, z1)-->t1, s3---fail(zone, false)-->s3},   {---:hb_B:13:1-->},
+   [((t<GET_MAX z))/\((tick(z, t, z1)=:ra:11:1))
+     /\((:ra:11:1=tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
+     /\((fail(zone, false)=:ra:12:1))/\((:ra:12:1=fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
+     /\((:hb_B:13:1=fail(b0:sva_SV0:1:1)))/\((b1:sva_SV0:1:1->b0:sva_SV0:1:1)
+     /\(z1:sva_SV0:1:1=z:sva_SV0:1:1/\(((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt)))+t:sva_SV0:1:1)))
+     /\((alpha0=:ra:1:1))],   {t := (t+1), z := z1}
+    OT10 ------------------------------------------------------------
+        <t1_s3>-----:ra:1:1----><t1_s3>
+
+INFO  BIPArchFailureTimerMax_LTF3 -
+   {t1---cancel(false)-->t1, s3---resume(false)-->s3},   {---:hb_B:17:3-->},
+   [((cancel(false)=:ra:15:1))/\((:ra:15:1=cancel(b1:sva_SV1:1:2)))
+     /\((resume(false)=:ra:16:1))/\((:ra:16:1=resume(b2:sva_SV1:1:2)))
+     /\((:hb_B:17:3=resume))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2))/\((alpha1=:ra:1:2))],   {}
+    OT11 ------------------------------------------------------------
+        <t1_s3>-----:ra:1:2----><t1_s3>
+
+INFO  BIPArchFailureTimerMax_LTF3 -
+   {s3---reset-->s1},   {---:hb_E:116:8-->},
+   [((reset=:ra:114:1))/\((:ra:114:1=reset))/\((:hb_E:116:8=reset))/\((alpha3=:ra:1:4))],   {}
+    OT12 ------------------------------------------------------------
+        <t1_s3>-----:ra:1:4----><t1_s1>
+
+INFO  BIPArchFailureTimerMax_LTF3 - Total: 12 SATISFIABLE OTs
+INFO  BIPArchFailureTimerMax_LTF3 -        235 UNSATISFIABLE OTs
+INFO  BIPArchFailureTimerMax_LTF3 - Total Time: 1293 ms
+\end{verbatim}
+
+OTs simplifiees a la main:
+
+$  OT_1  = \openrule
+{\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
+{\ostate{00} \OTarrow{\underline{\alpha_4}} \ostate{11}}
+$
+\medskip
+
+$  OT_2  = \openrule
+{\{B\mapsto fail(b0)\},\\
+  t<GetMax(z) \land b1=false \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),
+  \{z:=z1\} }
+{\ostate{11} \OTarrow{\underline{\alpha_0}} \ostate{11}}
+$
+\medskip
+
+  $  OT_3  = \openrule
+  {\{B\mapsto fail(b0)\},\\
+    t<GetMax(z) \land b1=true \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),
+    \{z:=z1\} }
+  {\ostate{11} \OTarrow{\underline{\alpha_0}} \ostate{12}}
+  $
+  \medskip
+
+  $  OT_4  = \openrule
+  {\{B\mapsto resume\},
+    b1=false \land b2=false \land b1=b2
+    \{\}  }
+  {\ostate{11} \OTarrow{\underline{\alpha_1}} \ostate{11}}
+  $
+  \medskip
+
+  $  OT_5  = \openrule
+  {\{E\mapsto ask\},
+    t \in z,
+    \{t:=t+1\}  }
+  {\ostate{11} \OTarrow{\underline{\alpha_2}} \ostate{11}}
+  $
+  \medskip
+
+  $  OT_7  = \openrule
+  {\{B\mapsto resume\},
+    b1=false \land b2=false \land b1=b2,
+    \{\} }
+  {\ostate{12} \OTarrow{\underline{\alpha_1}} \ostate{12}}
+  $
+  \medskip
+
+  $  OT_8  = \openrule
+  {\{B\mapsto resume\},
+    b1=true \land b2=true \land b1=b2, 
+    \{t:=0, z:=TopInt\} }
+  {\ostate{12} \OTarrow{\underline{\alpha_1}} \ostate{11}}
+  $
+  \medskip
+
+  $  OT_9  = \openrule
+  {\{E\mapsto ask\},
+    t \in z,
+    \{t:=t+1\} }
+  {\ostate{12} \OTarrow{\underline{\alpha_2}} \ostate{13}}
+  $
+  \medskip
+
+  $  OT_{10}  = \openrule
+  {\{B\mapsto fail(b0)\},\\
+    t<GetMax(z) \land b1=false \land b1=>b0 \land z1=(z \cap (b1?zone;TopInt)+t),
+    \{t:=t+1, z:=z1\} }
+  {\ostate{13} \OTarrow{\underline{\alpha_0}} \ostate{13}}
+  $
+  \medskip
+
+  $  OT_{11}  = \openrule
+  {\{B\mapsto resume\},
+    b1=false \land b2=false \land b1=b2,
+    \{\} }
+  {\ostate{13} \OTarrow{\underline{\alpha_1}} \ostate{13}}
+  $
+  \medskip
+
+  $  OT_{12}  = \openrule
+  {\{E\mapsto reset\},
+    true,
+    \{\} }
+  {\ostate{13} \OTarrow{\underline{\alpha_3}} \ostate{11}}
+  $
+
 \end{document}

### 2018-12-18 2016-Weak-FH-Bisim/WeakBisim.tex
input variables
Lemma OT decomposition

--- 2018-11-22 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 $\vars(t)$ identifies the set of variables in a term
-$t\in\AlgT$, and $iv(t)$ returns its input variables.
+$t\in\AlgT$, and $iv(t)$ returns the name of its input variables (without the '?' marker).
 Action algebras can encode naturally usual point-to-point message passing calculi (using 
@@
 \begin{array}{l}
-\Sortop(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{x \gets ?x| 
+\Sortop(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{?x \gets x| 
 x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
@@
 \end{lemma}
-\LUDO{A V2 by Ludo}
 
@@
 By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
-$ \forall i \in [0\ldots n]	\,		
-	P[Q]_{j_0}	\models		
+$ \forall i\! \in [0\ldots m_1]\,		
+	P[Q]_{j_0}\!\models		
 \openrule
@@
          {\ostate{s^1_i} \OTarrow {\tau} \ostate{s^1_{i+1}}}$
-~and~ $\forall i \in [0\ldots m] \, P[Q]_{j_0}	\models \openrule
+~and~ $\forall i \in [0\ldots m_2] \,\, P[Q]_{j_0}\!\models \openrule
          {
@@
 $
-s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
-\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i}}}
+s=s^1_0 \wedge s^1_{m_1}=s^2 \wedge s'^2 = s^3_0 \wedge s^3_{m_2}=s',
+\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i}}}
 \\
-\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\bigotimes_{i=0}^{n}\subst{\Post_i^1}\land (\bigwedge_{i=0}^m\Pred\,^3_i\subst{\Post^2})\bigotimes_{i=0}^{n}\subst{\Post^1_i}\\
-\Post=\biguplus_{i=0}^{m}(\Post^3_i\subst{\Post^2})\bigotimes_{i=0}^{n}\subst{\Post^1_i}
+\Pred=\bigwedge_{i=0}^{m_1}\Pred^1_i\land\Pred\,^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land (\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2})\bigotimes_{i=0}^{m_1}\subst{\Post^1_i}\\
+\Post=\biguplus_{i=0}^{m_2}(\Post^3_i\subst{\Post^2})\bigotimes_{i=0}^{m_1}\subst{\Post^1_i}
 $
@@
 \begin{enumerate}
-\item For  $\symb{OT}$ in the form: 
+\item For each open transition  $\symb{OT}_p$ in the form: 
 $P[Q]_{j_0}	\models		\openrule
@@
          {\ostate{s_p} \OTarrow {\tau} \ostate{s^1_{p+1}}}$ \\
-We obtain:\\
+we obtain by Lemma \ref{lem-decompose}:\\
 $P\models{\openrule
@@
 		}%\]
-	\,\text{~~and~~}
+	\,\text{~~and~~} \left\{
+  \begin{array}{l}
 		%\[
@@
 			{
-				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {\Pred_p''},  
-				{\Post_p''}}
-			{\ostate{(s_{p})_l^{l\in L_Q}} \OTarrow {\alpha_p}
-				\ostate{({s_{(p+1)}})_l^{l\in L_Q}}}
-		}%\]
-		$\\
-and  $\Pred_p \iff {\Pred_p}\!\!'
+				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
+				{{\Post_p}\!\!''}}
+				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
+				\ostate{s_{(p+1)l}^{l\in L_Q}}}
+				}\\%\]\\
+				or\\
+		\openrule
+         {
+           (j\mapsto\tau)^{j\in L\cap\Holes(Q)},\True,\Id(s_{pl}^{l\in L_Q})}
+         {s_{pl}^{l\in L_Q} \OTarrow {\tau} s_{pl}^{l\in L_Q}}
+
+\end{array}
+\right.$\\
+such that  $\Pred_p \iff {\Pred_p}\!\!'
 		\land {\Pred_p}\!\!''\land \alpha_p=\beta_{pj_0}$, $\Post_p={\Post_p}\!\!'\uplus 
-		{\Post_p}\!\!''$ where ${\Post_p''}$ is the restriction of $\Post_p$ over variables of $\Leaves(Q)$.
-\item For $\symb{OT}$ in the form: $P[Q]_{j_0}	\models \openrule
+		{\Post_p}\!\!''$ where ${{\Post_p}\!\!''}$ is the restriction of $\Post_p$ over variables of $\Leaves(Q)$.
+\item Similarly, for the open transition $\symb{OT}$ in the form: $P[Q]_{j_0}	\models \openrule
          {
@@
          {\ostate{s} \OTarrow {\alpha} \ostate{s'}}$\\
-We obtain:\\
+We obtain by Lemma \ref{lem-decompose}:\\
 $
@@
 	\,\text{~~and~~}
+	 \left\{
+  \begin{array}{l}
 		%\[
@@
 				\ostate{s_l'^{\,l\in L_Q}}}
-		}%\]
+		}\\%\]
+	or\\
+		\openrule
+         {
+          (j\mapsto\tau)^{j\in L\cap\Holes(Q)},\True,\Id(s_{pl}^{l\in L_Q})}
+         {s_{pl}^{l\in L_Q} \OTarrow {\tau} s_{pl}^{l\in L_Q}}
+
+\end{array}
+\right.	
 		$
-		and  $\Pred \iff {\Pred}\,'
+such that  $\Pred \iff {\Pred}\,'
 		\land {\Pred}\,''\land \alpha'=\beta_{j_0}$, $\Post={\Post}\,'\uplus 
 		{\Post}\,''$ where ${\Post}\,''$ is the restriction of $\Post$ over variables of $\Leaves(Q)$.
-
 \end{enumerate}
 By using  Lemma \ref{lem-rel-OT-WOT} we can conclude that we have:
-
 \begin{mathpar}
@@
 				\Post\,'}
-			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
-				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
+			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
+				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
 		}%\]
 \end{mathpar}
-
-Where \TODO{I will add the rest}
-
-Considering the set of $\symb{OT}_p$ of $Q$ such that $p \in [0\ldots m+n+1]$, at each time a single open transition moves.   So we have for each open transition:
-
+Considering each  $\symb{OT}_p$ of $Q$ such that $p \in S$ and $S \subseteq [0\ldots (m_1\!+\!m_2)\!+\!1]$, the set of open transition that moves at each time, i.e,  the open transition $\symb{OT}_p$ in the form:
 \begin{mathpar}
@@
 			{
-				\beta_{pj}^{j\in J\cap\Holes(Q)}, {\Pred_p},  
+				(\beta_p)_j^{J_p}, {\Pred_p},  
 				{\Post_p}}
@@
 
-By definition \ref{def:buildweakOT} we can conclude that we have for all $p\in[0\ldots n+m]$:
-
+By rule (\WTTrois)  we can conclude that for each $p\in S$ we have:
 \begin{mathpar}
@@
 			{
-				{\gamma_{pj}^{j\in J_p}}, {\Pred_p},  
-				{\Post_p}'}
+			(\gamma_p)_j^{J_p}, {\Pred_p}, {\Post_p}}
 			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha_{p}}
@@
 		}%\]
-
-\end{mathpar}
-
-Where $J_p = J\cap\Holes(Q)$, ???? $\gamma_{pj}=\vis{\beta_{pj}}$,\\  $\Pred \iff \Pred\,'
+\end{mathpar}
+such that $\gamma_p = \vis{\beta_p}$.\\
+\TODO{maybe it is better to use $\gamma_p=[\beta_p]$}\\
+
+For  $\gamma_{j_0}=[\beta_0..\beta_n]$ we have $n$ open transitions  $\symb{OT}_p$ s.t $p\in [0\ldots n]$.
+
+Hence, we have forall $p\in [0\ldots n]$ :  
+\begin{mathpar}
+Q\models{\openrule
+			{
+			(\gamma_p)_j^{J_p}, {\Pred_p}, {\Post_p}}
+			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha_{p}}
+				\ostate{s_{(p+1)l}^{l\in L_Q}}}
+		}%\]
+\end{mathpar}
+and $\displaystyle{\bigcup_{p=0}^nJ_{p}} = J\cap\Holes(Q)$, $\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}}$, $\forall l\in L_Q,\, s_{0l}=s_l$, $s_{(n+1)l}=s'_l$  \\
+  $\Pred \iff \Pred\,'
 		\land \displaystyle{\bigvee_{p=0}^n}(\alpha_p= \beta_{pj_0}\land \Pred_p), \text{and~}
 \Post=\Post\,'\uplus\biguplus_{p=0}^n
-		\Post_p$
+		\Post_p \quad$
+
+\TODO{END???}
 

### 2018-12-19 2016-Weak-FH-Bisim/WeakBisim.tex
add in {T} inside OT

--- 2018-11-29 2016-Weak-FH-Bisim/WeakBisim.tex
@@
  and  \\
- $\Pred_{s,t} \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-   \left( \forall j. \beta_j=\beta_{jx}  \Rightarrow \Pred_{OT_x}
+ $\Pred_{s,t} \land \Pred_{OT}\implies$\\
+%\hspace{1cm}
+ $\bigvee_{x\in X}
+   \left( \forall j. \beta_j=\beta_{jx}  \land \Pred_{OT_x}
      \land \alpha\!=\!\alpha_x \land  
@@
      %     \right)$.
+\bigskip
+
+ $\Pred_{s,t} \land \Pred_{OT}\implies\bigvee_{x\in X} \Pred_x$\\
+and
+%\hspace{1cm}
+ $ \forall{x\in X}. \Pred_x \land \Pred_{s,t} \land \Pred_{OT} \Rightarrow
+   \left( \forall j. \beta_j=\beta_{jx}  \land \Pred_{OT_x}
+     \land \alpha\!=\!\alpha_x \land  
+     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
+     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
+     %     \right)$.
+
+\medskip
+
+Idea: we define $OT\implies OT$ to check whether an OT is a particular case of another one (refining free action variables and predicates)
+ \begin{mathpar}
+    \openrule
+         {
+           \beta_{j}^{j\in J_{x}}, \Pred_{OT},\subst{x_k\leftarrow e_k}^{k\in K}}
+          {t \OTarrow {\alpha} t'}
+\implies
+    \openrule
+         {
+           (\beta_{j}\Post)^{j\in J}, \Pred_{OT}\Post\land\Pred,\subst{x_k\leftarrow e_k\Post}^{k\in K}}
+         {t \OTarrow {\alpha\Post} t'}
+\end{mathpar}
+
+\medskip
 

### 2018-12-19 2018-Arch-pNets/arch-pNets.tex

@@
   \label{OT:enable-composed}
-  \todoEM{Commenter...}
+  \todoEM{Commenter...
+  Questions: les $\alpha$ n'apparaissent pas dans l'archi Bip; la
+  synchro des initialisations non plus... OT3 est un peu plus facile a
+  expliquer (;-).}
   The \texttt{Failure TimerMonitor} pNet of \Fig{FailureTimer:pNet} has 2 controllers 
@@
 \end{example}
+
+The first one, $OT_1$, corresponds to the simultaneous initialisation
+of both controlers. No hole is active at that time, and the resulting
+global action is denoted $\alpha_4$.
+
+The second one, $OT_3$, correspond to the firing of the connector
+$''tick, fail, fail''$, with the hole B performing action $fail$......
 

### 2018-12-19 2018-Arch-pNets/arch-pNets.tex
Arch-pNets paper: added four example formulas satisfied (allegedly) by the Failure Monitor architecture

@@
 
+%% CTL
+\newcommand{\AG}[1][\ ]{\ensuremath{\mathtt{AG}#1}}
+\newcommand{\AF}[1][\ ]{\ensuremath{\mathtt{FG}#1}}
+\newcommand{\EF}[1][\ ]{\ensuremath{\mathtt{EF}#1}}
+\newcommand{\AW}[3][\ ]{\ensuremath{\mathtt{A}\left[#2\ \mathtt{W}\ #3\right]#1}}
+
 \newcommand{\filter}[2][]{\ensuremath{\pi_{#1}({#2})}}
@@
 have $(\emptyset, \true, \noop) \in \Gamma$.
+
+\begin{example}
+  The architecture in \fig{schema:ArchFailure:BIP} enforces the
+  following properties:
+  \begin{enumerate}
+  \item There is always a possibility to reset the system after a
+    failure:
+    \begin{equation}
+      \label{eq:prop:reset:can}
+      \AG (\PortFail \rightarrow \EF \PortReset).
+    \end{equation}
+  \item Whenever a reset is requested, it will eventually be
+    effectuated:
+    \begin{equation}
+      \label{eq:prop:reset:will}
+      \AG (\PortAsk \rightarrow \AF \PortReset).
+    \end{equation}
+  \item As long as no failure has occured, the $z$ variable of the
+    $\NameTimer$ component has the value $\topinterval$:
+    \begin{equation}
+      \label{eq:prop:z:top}
+      \AW[\quad]{(z = T)}{\PortFail} \land\quad
+      \AG \bigl(
+      \PortReset \rightarrow \AW[]{(z = T)}{\PortFail}
+      \bigr).
+    \end{equation}
+  \item A timeout can only occur within the specified delay after
+    a failure:
+    \begin{multline}
+      \label{eq:prop:to:delay}
+      \forall T_0, T_1 \in \sZ,\
+      \AG \Big((\PortFail \land \NameTimer.t = T_0) \rightarrow
+      \\
+      \AW[]{\bigl((\PortTO \land \NameTimer.t = T_1) \rightarrow
+        (T_1 - T_0 \in \NameCtrl.\mathit{zone})\bigr)
+      }{
+        (\PortReset \lor \PortResume)
+      }\Big),
+    \end{multline}
+    where $T_0$ and $T_1$ are integer parameters.  (The formula
+    holds with the universal quantification over $T_0$ and $T_1$
+    due to the fact that their individual values only appear in
+    the left-hand sides of the two implications.)
+  \end{enumerate}
+\end{example}
 

### 2018-12-19 2016-Weak-FH-Bisim/WeakBisim.tex
add in T inside T implied rule
RE INDEXATION DES  etats

--- 2018-12-18 2016-Weak-FH-Bisim/WeakBisim.tex
@@
      %     \right)$.
+\bigskip
+
+ $\Pred_{s,t} \land \Pred_{OT}\implies\bigvee_{x\in X} \Pred_x$\\
+and
+%\hspace{1cm}
+ $ \forall{x\in X}. \Pred_x \land \Pred_{s,t} \land \Pred_{OT} \Rightarrow
+   \left( \forall j. \beta_j=\beta_{jx}  \land \Pred_{OT_x}
+     \land \alpha\!=\!\alpha_x \land  
+     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
+     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
+     %     \right)$.
+
+\medskip
+
+Idea: we define $OT\implies OT$ to check whether an OT is a particular case of another one (refining free action variables and predicates)
+ \begin{mathpar}
+    \openrule
+         {
+           \beta_{j}^{j\in J_{x}}, \Pred_{OT},\subst{x_k\leftarrow e_k}^{k\in K}}
+          {t \OTarrow {\alpha} t'}\in\mathcal{T}
+\implies
+    \openrule
+         {
+           (\beta_{j}\Post)^{j\in J}, \Pred_{OT}\Post\land\Pred,\subst{x_k\leftarrow e_k\Post}^{k\in K}}
+         {t \OTarrow {\alpha\Post} {t'}}\in\mathcal{T}
+\end{mathpar}
+
+\medskip
 
@@
     		\ostate{s_m'}} }\\\\
-     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
+%     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J \frac{num}{den}	\\
     	\Pred = \bigwedge_{m\in I_1\uplus I_2}\!\! \Pred_m \land
@@
 This theorem is quite powerful somehow states that the theory of open pNets is convenient to study properties of process composition.
-Open pNets can indeed be used to study process operators and process algebras, as shown in~\cite{henrio:Forte2016}, or to study interaction protocols \TODO{ref vers ABP?}
+Open pNets can indeed be used to study process operators and process algebras, as shown in~\cite{henrio:Forte2016}, or to study interaction protocols \TODO{ref vers fault tolerance byzantine FACS 2011}
 
@@
 \]
-\TODO{question : it looks like we can have 2 holes doing a tau and observe this ; I belive this is not safe (LUDO)}
+\TODO{question : it looks like we can have 2 holes doing a tau and observe this ; I belive this is not safe TODO LUDO add a $A(j)=\tau$}
 \end{enumerate}
@@
 
+       \section{Weak FH-bisimulation lemmas and proofs}
+
 \TODO{Voir ou ajouter ceci: We introduce the notation ${\displaystyle \bigotimes_{i=1}^{n} \subst{Post_i}}$ to denote a combination of multiple substitution operations}
-
-       \section{Weak FH-bisimulation lemmas and proofs}
-
 \subsection{Weak bisimulation is an equivalence}
@@
 	\]
-		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction. Suppose $\gamma_{j_0}=[\beta_0..\beta_n]$
-		 then there exist $\Pred\,'$,  
+		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.  
+		 Then there exist $\gamma_{j_0}=[\beta_0..\beta_n]$, $\Pred\,'$,  
 		$\Post\,'$,   and for all $p\in[0..n]$ there exist $\alpha_p$, $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
@@
 				\Post}
-			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
-				\ostate{s_i'^{\, i\in L}}} 
+			{\ostate{s_l^{l\in L}} \OTWeakarrow {\alpha}
+				\ostate{s_l'^{\, l\in L}}} 
 \end{mathpar}
@@
        \set{(\beta^1_i)},\Pred^1_i,\Post^1_i   }
-         {\ostate{s^1_i} \OTarrow {\tau} \ostate{s^1_{i+1}}}$
+         {\ostate{s^{l\in L}_{il}} \OTarrow {\tau} \ostate{s^{l\in L}_{(i+1)l}}}$
 ~and~ $\forall i \in [0\ldots m_2] \,\, P[Q]_{j_0}\!\models \openrule
@@
            \set{(\beta^3_i)},\Pred\,^3_i, \Post_i^3   }
-         {\ostate{s^3_i} \OTarrow {\tau} \ostate{s^3_{i+1}}}
+         {\ostate{u^{l\in L}_{il}} \OTarrow {\tau} \ostate{u^{l\in L}_{(i+1)l}}}
 $\\
@@
            \set{\beta^2},\Pred\,^2,\Post^2 }
-         {\ostate{s^2} \OTarrow {\alpha} \ostate{s'^2}}
-$ where\\
+         {\ostate{t_l^{l\in L}} \OTarrow {\alpha} \ostate{{t'}_l^{l\in L}}}
+$ where for all $l\in L$\\
 $
-s=s^1_0 \wedge s^1_{m_1}=s^2 \wedge s'^2 = s^3_0 \wedge s^3_{m_2}=s',
+s_j=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l,
 \displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i}}}
@@
 \Pred=\bigwedge_{i=0}^{m_1}\Pred^1_i\land\Pred\,^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land (\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2})\bigotimes_{i=0}^{m_1}\subst{\Post^1_i}\\
-\Post=\biguplus_{i=0}^{m_2}(\Post^3_i\subst{\Post^2})\bigotimes_{i=0}^{m_1}\subst{\Post^1_i}
+\Post=(\bigotimes_{i=0}^{m_2}\Post^3_i)\subst{\Post^2}\bigotimes_{i=0}^{m_1}\subst{\Post^1_i}
 $
@@
        \set{\beta}_p,\Pred_p,\Post_p   }
-         {\ostate{s_p} \OTarrow {\tau} \ostate{s^1_{p+1}}}$ \\
-we obtain by Lemma \ref{lem-decompose}:\\
+         {\ostate{s_p^1} \OTarrow {\tau} \ostate{s^1_{p+1}}}$ \\
+If $Q$ moves then we obtain by Lemma \ref{lem-decompose}:\\
 $P\models{\openrule
@@
 				{\Post_p}\!\!'}
-			{\ostate{(s_{p})_l^{l\in L\setminus L_Q}} \OTarrow {\tau}
-				\ostate{({s}_{p}')_l^{l\in L\setminus L_Q}}}
+			{\ostate{s_{p l}^{l\in L\setminus L_Q}} \OTarrow {\tau}
+				\ostate{({s_{(p+1) l}})^{l\in L\setminus L_Q}}}
 		}%\]
 	\,\text{~~and~~} \left\{
-  \begin{array}{l}
-		%\[
 		Q\models{\openrule
@@
 				}\\%\]\\
-				or\\
-		\openrule
-         {
-           (j\mapsto\tau)^{j\in L\cap\Holes(Q)},\True,\Id(s_{pl}^{l\in L_Q})}
-         {s_{pl}^{l\in L_Q} \OTarrow {\tau} s_{pl}^{l\in L_Q}}
-
-\end{array}
 \right.$\\
+Else $Q$ does not move and \\
+$P\models{\openrule
+			{
+				(\beta_{p})_j^{j\in (J\setminus \Holes(Q)) }, 
+				{\Pred_p},  
+				{\Post_p}}
+			{\ostate{(s_{p l})^{l\in L\setminus L_Q}} \OTarrow {\tau}
+				\ostate{({s}_{(p+1) l})^{l\in L_Q}}}
+		}$~~and~~ $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}} $
 such that  $\Pred_p \iff {\Pred_p}\!\!'
@@
 		{\Post_p}\!\!''$ where ${{\Post_p}\!\!''}$ is the restriction of $\Post_p$ over variables of $\Leaves(Q)$.
+
+LUDO STOPPED HERE
+
 \item Similarly, for the open transition $\symb{OT}$ in the form: $P[Q]_{j_0}	\models \openrule

### 2018-12-20 2016-Weak-FH-Bisim/WeakBisim.tex
todos de la reunion
yet lemma 5

@@
 
+TODOs du 19 decembre
+
+- TROUVER UN EXEMPLE ET LE METTRE DANS L ARTICLE
+
+- enlever 5.2 et citer avocs
+
+- ajouter des proof sketch dans le papier
+
+- def 11 point 2:
+A, Pred, Post
+-----------   in T
+s->s'
+et A(j)=tau
+implies blablabla
+
+- adopter la def semantique d ot pour la bisim
+
+OLD OLD OLD (check)
 Notes de reunion 24 Sept
@@
 		}%\]
-	\,\text{~~and~~} \left\{
+	\,\text{~~and~~} 
 		Q\models{\openrule
@@
 				}\\%\]\\
-\right.$\\
+$\\
 Else $Q$ does not move and \\
@@
            \set{\beta},\Pred,\Post }
-         {\ostate{s} \OTarrow {\alpha} \ostate{s'}}$\\
-We obtain by Lemma \ref{lem-decompose}:\\
+         {\ostate{t} \OTarrow {\alpha} \ostate{t'}}$\\
+If $Q$ moves then we  obtain by Lemma \ref{lem-decompose}:\\
 $
@@
 				{\Post}\,'}
-			{\ostate{s_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
-				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
+			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
+				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
 		}%\]
 	\,\text{~~and~~}
-	 \left\{
-  \begin{array}{l}
-		%\[
 	Q\models{\openrule
@@
 				{\Post}\,''}
-			{\ostate{s_l^{l\in L_Q}} \OTarrow {\alpha'}
-				\ostate{s_l'^{\,l\in L_Q}}}
+			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'}
+				\ostate{t_l'^{\,l\in L_Q}}}
 		}\\%\]
-	or\\
-		\openrule
-         {
-          (j\mapsto\tau)^{j\in L\cap\Holes(Q)},\True,\Id(s_{pl}^{l\in L_Q})}
-         {s_{pl}^{l\in L_Q} \OTarrow {\tau} s_{pl}^{l\in L_Q}}
-
-\end{array}
-\right.	
 $
+Else $Q$ does not move we  \\
+$
+		P\models{\openrule
+			{
+				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
+				{\Pred}\,',  
+				{\Post}\,'}
+			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
+				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
+		}%\]
+	\,\text{~~and~~} \ostate{t_l^{l\in L_Q}} = 
+				\ostate{t_l'^{\,l\in L_Q}}$
 such that  $\Pred \iff {\Pred}\,'
@@
 \end{enumerate}
-By using  Lemma \ref{lem-rel-OT-WOT} we can conclude that we have:
+By using  Lemma \ref{lem-rel-OT-WOT} we can conclude from case 1 and 2 that we have:
 \begin{mathpar}
@@
 \end{mathpar}
-Considering each  $\symb{OT}_p$ of $Q$ such that $p \in S$ and $S \subseteq [0\ldots (m_1\!+\!m_2)\!+\!1]$, the set of open transition that moves at each time, i.e,  the open transition $\symb{OT}_p$ in the form:
+
+\TODO{We will add side conditions ?? }\\
+Concerning $Q$ if it moves, for each  $\symb{OT}_p$ of $Q$ such that $p \in S$ and $S \subseteq [0\ldots (m_1\!+\!m_2)\!+\!1]$ in the form:
 \begin{mathpar}
@@
 \end{mathpar}
-
-By rule (\WTTrois)  we can conclude that for each $p\in S$ we have:
+By rule (\WTTrois)  we can conclude that  we have:
 \begin{mathpar}
@@
 \end{mathpar}
-such that $\gamma_p = \vis{\beta_p}$.\\
+such that $\gamma_p = \vis{\beta_p}$.
 \TODO{maybe it is better to use $\gamma_p=[\beta_p]$}\\

### 2018-12-20 2016-Weak-FH-Bisim/WeakBisim.tex
skype with rabea

@@
 By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
-$ \forall i\! \in [0\ldots m_1]\,		
+$ \forall p\! \in [0\ldots m_1]\,		
 	P[Q]_{j_0}\!\models		
@@
     {
-       \set{(\beta^1_i)},\Pred^1_i,\Post^1_i   }
-         {\ostate{s^{l\in L}_{il}} \OTarrow {\tau} \ostate{s^{l\in L}_{(i+1)l}}}$
+       \set{(\beta^1_p)},\Pred^1_p,\Post^1_p   }
+         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$
 ~and~ $\forall i \in [0\ldots m_2] \,\, P[Q]_{j_0}\!\models \openrule
          {
-           \set{(\beta^3_i)},\Pred\,^3_i, \Post_i^3   }
-         {\ostate{u^{l\in L}_{il}} \OTarrow {\tau} \ostate{u^{l\in L}_{(i+1)l}}}
+           \set{(\beta^3_p)},\Pred\,^3_p, \Post_p^3   }
+         {\ostate{u^{l\in L}_{pl}} \OTarrow {\tau} \ostate{u^{l\in L}_{(p+1)l}}}
 $\\
@@
          {\ostate{t_l^{l\in L}} \OTarrow {\alpha} \ostate{{t'}_l^{l\in L}}}
-$ where for all $l\in L$\\
 $
-s_j=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l,
-\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i}}}
+
+where for all $l\in L$:\\
+$
+s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
+$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i}}}
 \\
@@
 \item For each open transition  $\symb{OT}_p$ in the form: 
-$P[Q]_{j_0}	\models		\openrule
-    {
-       \set{\beta}_p,\Pred_p,\Post_p   }
-         {\ostate{s_p^1} \OTarrow {\tau} \ostate{s^1_{p+1}}}$ \\
+$P[Q]_{j_0}\!\models		
+\openrule
+    {
+       \set{(\beta^1_p)},\Pred^1_p,\Post^1_p   }
+         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$ \\
 If $Q$ moves then we obtain by Lemma \ref{lem-decompose}:\\
@@
 				}\\%\]\\
-$\\
+$
+
+such that  $\Pred^1_p \iff {\Pred_p}\!\!'
+		\land {\Pred_p}\!\!''\land \alpha_p=\beta_{pj_0}$, $\Post^1_p={\Post_p}\!\!'\uplus 
+		{\Post_p}\!\!''$ where ${{\Post_p}\!\!''}$ is the restriction of $\Post^1_p$ over variables of $\Leaves(Q)$.\\
 Else $Q$ does not move and \\
@@
 				(\beta_{p})_j^{j\in (J\setminus \Holes(Q)) }, 
-				{\Pred_p},  
-				{\Post_p}}
+				{\Pred^1_p},  
+				{\Post^1_p}}
 			{\ostate{(s_{p l})^{l\in L\setminus L_Q}} \OTarrow {\tau}
@@
 		}$~~and~~ $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}} $
-such that  $\Pred_p \iff {\Pred_p}\!\!'
-		\land {\Pred_p}\!\!''\land \alpha_p=\beta_{pj_0}$, $\Post_p={\Post_p}\!\!'\uplus 
-		{\Post_p}\!\!''$ where ${{\Post_p}\!\!''}$ is the restriction of $\Post_p$ over variables of $\Leaves(Q)$.
-
-LUDO STOPPED HERE
+
+\item similarly for tau transitions on states named $u$.
 
@@
          {
-           \set{\beta},\Pred,\Post }
+           \set{\beta^2},\Pred^2,\Post^2 }
          {\ostate{t} \OTarrow {\alpha} \ostate{t'}}$\\
@@
 				\ostate{t_l'^{\,l\in L_Q}}}
-		}\\%\]
-$
-Else $Q$ does not move we  \\
+		}%\]
+$\\
+such that  $\Pred^2 \iff {\Pred}\,'
+		\land {\Pred}\,''\land \alpha'=\beta_{j_0}$, $\Post^2={\Post}\,'\uplus 
+		{\Post}\,''$ where ${\Post}\,''$ is the restriction of $\Post^2$ over variables of $\Leaves(Q)$.
+
+Else $Q$ does not move and we have \\
 $
@@
 				\ostate{t_l'^{\,l\in L_Q}}$
-such that  $\Pred \iff {\Pred}\,'
-		\land {\Pred}\,''\land \alpha'=\beta_{j_0}$, $\Post={\Post}\,'\uplus 
-		{\Post}\,''$ where ${\Post}\,''$ is the restriction of $\Post$ over variables of $\Leaves(Q)$.
+
 \end{enumerate}

### 2019-01-07 2016-Weak-FH-Bisim/WeakBisim.tex
lemma 5 tentative

@@
 
-\item similarly for tau transitions on states named $u$.
-
-\item Similarly, for the open transition $\symb{OT}$ in the form: $P[Q]_{j_0}	\models \openrule
+\item Similarly for tau transitions on states named $u$.
+
+\item And, for the open transition $\symb{OT}$ in the form: $P[Q]_{j_0}	\models \openrule
          {
@@
 \end{enumerate}
+
 By using  Lemma \ref{lem-rel-OT-WOT} we can conclude from case 1 and 2 that we have:
@@
 \TODO{We will add side conditions ?? }\\
-Concerning $Q$ if it moves, for each  $\symb{OT}_p$ of $Q$ such that $p \in S$ and $S \subseteq [0\ldots (m_1\!+\!m_2)\!+\!1]$ in the form:
+
+Concerning $Q$, we consider only the paths for which it moves.
+So for each, state such that we have $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}}$, we skip the state $\ostate{({s}_{(p+1) l})^{l\in L_Q}}$ and  we rename all its following states  $\ostate{(s_{p})_l^{l\in L_Q}}$ by $\ostate{({s}_{(p-1) l})^{l\in L_Q}}$.
+We proceed in the same way as for states named $u$.
+
+Therefore, we will obtain:
+
+$\forall p \in [0\ldots n_1] Q\models{\openrule
+			{
+				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
+				{{\Post_p}\!\!''}}
+				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
+				\ostate{s_{(p+1)l}^{l\in L_Q}}}
+				}%\]
+$
+and
+$ Q\models{\openrule
+			{
+				\beta_j^{j\in J\cap\Holes(Q)}, {\Pred}\,'',  
+				{\Post}\,''}
+			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'}
+				\ostate{t_l'^{\,l\in L_Q}}}
+		}%\]
+$
+and
+$\forall p \in [0\ldots n_2] Q\models{\openrule
+			{
+				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
+				{{\Post_p}\!\!''}}
+				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha'_{p}}
+				\ostate{u_{(p+1)l}^{l\in L_Q}}}
+				}%\]
+$\\
+such that $n_1 \leq m_1$ and $n_2 \leq m_2$\\
+\TODO{We will discuss}
+
+For each  $\symb{OT}_p$ of $Q$ such that $p \in S$ and $S \subseteq [0\ldots (m_1\!+\!m_2)\!+\!1]$ in the form:
 \begin{mathpar}
@@
 		\Post_p \quad$
-
-\TODO{END???}
 

### 2019-01-17 2018-Arch-pNets/arch-pNets.tex
working on introduction

@@
 
-\title{Architectures and Open pNets}
+\title{BIP Architectures and Open pNets}
 
@@
   \and
+	Univ Lyon, CNRS, ENS de Lyon, Inria, Universit\'e Claude Bernard Lyon 1, LIP UMR 5668, Lyon, France\\\email{ludovic.henrio@ens-lyon.fr}
   \and
@@
 property, the resulting system satisfies their conjunction.
+
+This article goes one step further in the proof of properties and in the compositionality of architectures, but this step is a significant one as it targets verification and consequently compositional verification.
+To ensure properties of BIP architectures
+it is necessary to have a representation of the BIP architecture in a verifiable format. 
+The verification problem has two unbounded parameters: 1) By nature, architectures have holes and are meant to interact with the interfaces of the component that will fill the hole; the properties must hold for all (well-typed) components that can be put inside the hole; 2) BIP interactions can transmit data, and properties might be dependent of the data, the domain of the data is generally huge or unbound and the value of transmitted data might have a significant impact on the properties.
+
+Due to the nature of the problem, we propose to rely on a translation of BIP architectures into pNets, a direct verification of BIP could also be possible but pNets already have a verification tools based on a SMT solver, and doing the same work for BIP would require  a large amount of similar development.
+More interestingly, relying on a translation to pNets allow us to compare the two models, as discussed below.
+
+Parameterised Networks of synchronised automata (pNets) is a formalism for defining behavioural specification of distributed systems.
+It inherited from the work of
+Arnold on synchronisation vectors~\cite{Arnold1982}. 
+In previous work~\cite{HMZ:PDP15}, it was shown pNets can be used to represent the behavioural semantics
+of a system 
+including value-passing and many kinds of synchronisation methods. We
+used these results to give the semantics of various constructs and
+languages for distributed objects, and to build a platform for design
+and verification of distributed software components
+\cite{CM:FMCO08,HKM-FASE16}. 
+By nature, pNets is a  parametrised and hierarchical model.
+Their structure is static, but unbounded, and this allows for model-checking
+approaches even for reconfigurable applications.
+Closed pNets were used to encode fully defined programs or systems,
+while open pNets have ``holes'', playing the role of process
+parameters. Such open systems can be used to define composition operators or structuring architectures.
+It is possible to reason, in an SMT engine, on the symbolic automaton that represents the behaviour of a pNets with holes and that communicates value~\cite{AVOCS}.
+This encding of open pNets into Z3 that is under development is the starting point of this article.
+Our objective is to benefit from the possibility to reason on a pNet in an SMT engine in order to prove properties on BIP architectures.
+
+The methodology we propose is thus to an encoding of BIP architectures into open pNet in order to be able to verify, using SMT techniques, the coordination capabilities of the architecture, and more generally its properties.
+The encoding will also give us feedback on the comparison between the BIP architectures and the pNet formalism.
+Overall, the encoding allows us to precisely compare the coordination mechanisms of the two models but also the way component composition is expressed in the two formalisms.
+This article is also the opportunity to investigate further on  compositional verification by relating two different composition mechanisms that provide different vision on compositional verification.
+\textbf{pas tres heureux la fin: pas assez detaille ou trop complique -> abstraire ou detailller a mon avis (Ludo)}
+
+\paragraph{Contributions}
 

### 2019-01-18 2018-Arch-pNets/arch-pNets.tex
arch-pNets: (Minor) INRIA --> Inria
arch-pNets: Minor edits

@@
 \institute{%
-  INRIA Lille -- Nord Europe, Villeneuve d'Ascq, France\\
+  Inria Lille -- Nord Europe, Villeneuve d'Ascq, France\\
   \email{simon.bliudze@inria.fr}
@@
 example extending the Failure Monitor architecture from the CubETH
-nanosatellite on-board software case-study~\cite{CubETH-case-study}.
+nanosatellite on-board software case study~\cite{CubETH-case-study}.
 
@@
 
+%****************************************************************
+
+\subsection{Verification of the characteristic properties}
+\label{secn:arch:verif}
+
 \begin{figure}[t]
@@
 Should list some temporal logic properties....
+
+%****************************************************************
+
+\subsection{Composition of architectures}
+\label{secn:arch:composition}
 
@@
 
-\subsection{Full results of the use-case}
+\subsection{Full results of the case study}
 \label{secn:full-results}

### 2019-01-18 2018-Arch-pNets/arch-pNets.tex
arch-pNets: (Minor) Separated timeout port in Timer and Ctrl into timeout_T and timeout_C
Eric: nouveau listing pour les OTs du FailureTimer

@@
 \{t, z\},
-\{\PortTick, \PortCancel, \PortTO\},
+\{\PortTick, \PortCancel, \PortTOT\},
 \export[\NameTimer]
@@
 \{\mathit{zone}\},
-\{\PortReset, \PortFail, \PortResume, \PortTO\},
+\{\PortReset, \PortFail, \PortResume, \PortTOC\},
 \export[\NameCtrl]
@@
       \\
-      \AW[]{\bigl((\PortTO \land \NameTimer.t = T_1) \rightarrow
+      \AW[]{\bigl((\PortTOC \land \NameTimer.t = T_1) \rightarrow
         (T_1 - T_0 \in \NameCtrl.\mathit{zone})\bigr)
@@
 
-      \node[node distance=1cm] (ab) [below of=start] {\NameTimer.\PortTO};
-      \node[node distance=2.1cm] (ac) [right of=ab]{\NameCtrl.\PortTO};
+      \node[node distance=1cm] (ab) [below of=start] {\NameTimer.\PortTOT};
+      \node[node distance=2.1cm] (ac) [right of=ab]{\NameCtrl.\PortTOC};
       \node[node distance=1.5cm] (aa) [left of=ab]{\PortAsk};
@@
     \begin{tikzpicture}[shorten >=1pt,node distance=.7cm,>=stealth']
-      \node (start) {\color{red}\PortAsk\ \NameTimer.\PortTO\ \NameCtrl.\PortTO};
+      \node (start) {\color{red}\PortAsk\ \NameTimer.\PortTOT\ \NameCtrl.\PortTOC};
       \node()[below of=start]{};
@@
         \begin{aligned}
-          \NameCtrl.\PortTO &\Rightarrow
-          \PortAsk \land \NameTimer.\PortTO
-          \\
-          \NameTimer.\PortTO &\Rightarrow 
-          \PortAsk \land \NameCtrl.\PortTO
+          \NameCtrl.\PortTOC &\Rightarrow
+          \PortAsk \land \NameTimer.\PortTOT
+          \\
+          \NameTimer.\PortTOT &\Rightarrow 
+          \PortAsk \land \NameCtrl.\PortTOC
         \end{aligned}}
@@
           \PortAsk &\Rightarrow
-          \NameTimer.\PortTO \land \NameCtrl.\PortTO
+          \NameTimer.\PortTOT \land \NameCtrl.\PortTOC
           \\
           \true &\Rightarrow
-          \PortAsk \land \NameTimer.\PortTO
-          \land \NameCtrl.\PortTO
+          \PortAsk \land \NameTimer.\PortTOT
+          \land \NameCtrl.\PortTOC
         \end{aligned}
@@
 
--------------------------------------------
-INFO  BIPArchFailureTimerMax_LTF3 - Total: 12 OTs
 INFO  BIPArchFailureTimerMax_LTF3 -
-        {t0---init-->t1, s0---init-->s1},   {},   
-        [((init=:ra:117:1))/\((:ra:117:1=init))/\((init=:ra:118:1))/\((:ra:118:1=init))
-          /\((alpha4=:ra:1:5))],   {t := 0, z := TopInt, zone := minZone,maxZone}
+       {t0---init-->t1, s0---init-->s1},   {},  [true],
+       {t := 0, z := TopInt, zone := minZone,maxZone}
     OT1 ------------------------------------------------------------
-        <t0_s0>-----:ra:1:5----><t1_s1>
+        <t0_s0>-----alpha4----><t1_s1>
 
 INFO  BIPArchFailureTimerMax_LTF3 -
-     {t1---tick(z, t, z1)-->t1, s1---fail(zone, false)-->s1},   {---:hb_B:13:1-->},   
-     [((t<GET_MAX z))/\((tick(z, t, z1)=:ra:11:1))
-       /\((:ra:11:1=tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
-       /\((fail(zone, false)=:ra:12:1))
-       /\((:ra:12:1=fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))/\
-       ((:hb_B:13:1=fail(b0:sva_SV0:1:1)))/\((b1:sva_SV0:1:1->b0:sva_SV0:1:1)/\
-       (z1:sva_SV0:1:1=z:sva_SV0:1:1/\(((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt)))+t:sva_SV0:1:1)))
-       /\((alpha0=:ra:1:1))],
-   {t := (t+1), z := z1}
+       {t1---tick(z, t, z1)-->t1, s1---fail(zone, false)-->s1},   {---:hb_B-->},
+       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
+         /\((tick(z, t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
+         /\((fail(zone, false))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
+         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
+         /\(z1:sva_SV0:1:1=
+         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
+       {t := t+1, z := z1}
     OT2 ------------------------------------------------------------
-        <t1_s1>-----:ra:1:1----><t1_s1>
+        <t1_s1>-----alpha0----><t1_s1>
 
 INFO  BIPArchFailureTimerMax_LTF3 -
-   {t1---tick(z, t, z1)-->t1, s1---fail(zone, true)-->s2},   {---:hb_B:13:1-->},
-   [((t<GET_MAX z))/\((tick(z, t, z1)=:ra:11:1))
-     /\((:ra:11:1=tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
-     /\((fail(zone, true)=:ra:12:1))/\((:ra:12:1=fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
-     /\((:hb_B:13:1=fail(b0:sva_SV0:1:1)))/\((b1:sva_SV0:1:1->b0:sva_SV0:1:1)
-     /\(z1:sva_SV0:1:1=z:sva_SV0:1:1/\(((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt)))+t:sva_SV0:1:1)))
-     /\((alpha0=:ra:1:1))],   {t := (t+1), z := z1}
+       {t1---tick(z, t, z1)-->t1, s1---fail(zone, true)-->s2},   {---:hb_B-->},
+       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
+         /\((tick(z,t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
+         /\((fail(zone, true))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
+         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
+         /\(z1:sva_SV0:1:1=
+         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
+       {t := t+1, z := z1}
     OT3 ------------------------------------------------------------
-        <t1_s1>-----:ra:1:1----><t1_s2>
+        <t1_s1>-----alpha0----><t1_s2>
 
 INFO  BIPArchFailureTimerMax_LTF3 -
-   {t1---cancel(false)-->t1, s1---resume(false)-->s1},   {---:hb_B:17:3-->},
-   [((cancel(false)=:ra:15:1))/\((:ra:15:1=cancel(b1:sva_SV1:1:2)))
-     /\((resume(false)=:ra:16:1))/\((:ra:16:1=resume(b2:sva_SV1:1:2)))
-     /\((:hb_B:17:3=resume))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2))/\((alpha1=:ra:1:2))],   {}
+       {t1---cancel(false)-->t1, s1---resume(false)-->s1},   {---:hb_B-->},
+       [(:hb_B=fail(b0:sva_SV0:1:1)
+         /\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
+         /\((resume(false))=(resume(b2:sva_SV1:1:2)))
+         /\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],   {}
     OT4 ------------------------------------------------------------
-        <t1_s1>-----:ra:1:2----><t1_s1>
+        <t1_s1>-----alpha1----><t1_s1>
 
 INFO  BIPArchFailureTimerMax_LTF3 -
-{t1---timeout-->t1, s1---timeout-->s1},   {---:hb_E:112:6-->},
-[(t in z)/\((timeout=:ra:19:1))/\((:ra:19:1=timeout))
-/\((timeout=:ra:110:1))/\((:ra:110:1=timeout))/\((:hb_E:112:6=ask))/\((alpha2=:ra:1:3))], {t := (t+1)}
+       {t1---timeout-->t1, s1---timeout-->s1},   {---:hb_E-->},
+       [(:hb_E=ask)/\(t in z)],   {t := t+1}
     OT5 ------------------------------------------------------------
-        <t1_s1>-----:ra:1:3----><t1_s1>
+        <t1_s1>-----alpha2----><t1_s1>
 
 INFO  BIPArchFailureTimerMax_LTF3 -
-   {t1---tick(z, t, z1)-->t1, s2---fail(zone, false)-->s2},   {---:hb_B:13:1-->},
-   [((t<GET_MAX z))/\((tick(z, t, z1)=:ra:11:1))
-     /\((:ra:11:1=tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
-     /\((fail(zone, false)=:ra:12:1))/\((:ra:12:1=fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
-     /\((:hb_B:13:1=fail(b0:sva_SV0:1:1)))/\((b1:sva_SV0:1:1->b0:sva_SV0:1:1)
-     /\(z1:sva_SV0:1:1=z:sva_SV0:1:1/\(((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt)))+t:sva_SV0:1:1)))
-     /\((alpha0=:ra:1:1))],   {t := (t+1), z := z1}
+       {t1---tick(z, t, z1)-->t1, s2---fail(zone, false)-->s2},   {---:hb_B-->},
+       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
+         /\((tick(z, t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
+         /\((fail(zone, false))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
+         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
+         /\(z1:sva_SV0:1:1=
+         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
+       {t := t+1, z := z1}
     OT6 ------------------------------------------------------------
-        <t1_s2>-----:ra:1:1----><t1_s2>
+        <t1_s2>-----alpha0----><t1_s2>
 
 INFO  BIPArchFailureTimerMax_LTF3 -
-   {t1---cancel(false)-->t1, s2---resume(false)-->s2},   {---:hb_B:17:3-->},
-   [((cancel(false)=:ra:15:1))/\((:ra:15:1=cancel(b1:sva_SV1:1:2)))
-     /\((resume(false)=:ra:16:1))/\((:ra:16:1=resume(b2:sva_SV1:1:2)))
-     /\((:hb_B:17:3=resume))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2))/\((alpha1=:ra:1:2))],   {}
+       {t1---cancel(false)-->t1, s2---resume(false)-->s2},   {---:hb_B-->},
+       [(:hb_B=resume)/\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
+         /\((resume(false))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],   {}
     OT7 ------------------------------------------------------------
-        <t1_s2>-----:ra:1:2----><t1_s2>
+        <t1_s2>-----alpha1----><t1_s2>
 
 INFO  BIPArchFailureTimerMax_LTF3 -
-   {t1---cancel(true)-->t1, s2---resume(true)-->s1},   {---:hb_B:17:3-->},
-   [((cancel(true)=:ra:15:1))/\((:ra:15:1=cancel(b1:sva_SV1:1:2)))
-     /\((resume(true)=:ra:16:1))/\((:ra:16:1=resume(b2:sva_SV1:1:2)))
-     /\((:hb_B:17:3=resume))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2))/\((alpha1=:ra:1:2))],
+       {t1---cancel(true)-->t1, s2---resume(true)-->s1},   {---:hb_B-->},
+       [(:hb_B=resume)/\((cancel(true))=(cancel(b1:sva_SV1:1:2)))
+         /\((resume(true))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],
        {t := 0, z := TopInt}
     OT8 ------------------------------------------------------------
-        <t1_s2>-----:ra:1:2----><t1_s1>
+        <t1_s2>-----alpha1----><t1_s1>
 
 INFO  BIPArchFailureTimerMax_LTF3 -
-   {t1---timeout-->t1, s2---timeout-->s3},   {---:hb_E:112:6-->},
-   [(t in z)/\((timeout=:ra:19:1))/\((:ra:19:1=timeout))
-     /\((timeout=:ra:110:1))/\((:ra:110:1=timeout))/\((:hb_E:112:6=ask))/\((alpha2=:ra:1:3))],
-   {t := (t+1)}
+       {t1---timeout-->t1, s2---timeout-->s3},   {---:hb_E-->},
+       [(:hb_E=ask)/\(t in z)],   {t := t+1}
     OT9 ------------------------------------------------------------
-        <t1_s2>-----:ra:1:3----><t1_s3>
+        <t1_s2>-----alpha2----><t1_s3>
 
 INFO  BIPArchFailureTimerMax_LTF3 -
-   {t1---tick(z, t, z1)-->t1, s3---fail(zone, false)-->s3},   {---:hb_B:13:1-->},
-   [((t<GET_MAX z))/\((tick(z, t, z1)=:ra:11:1))
-     /\((:ra:11:1=tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
-     /\((fail(zone, false)=:ra:12:1))/\((:ra:12:1=fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
-     /\((:hb_B:13:1=fail(b0:sva_SV0:1:1)))/\((b1:sva_SV0:1:1->b0:sva_SV0:1:1)
-     /\(z1:sva_SV0:1:1=z:sva_SV0:1:1/\(((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt)))+t:sva_SV0:1:1)))
-     /\((alpha0=:ra:1:1))],   {t := (t+1), z := z1}
+       {t1---tick(z, t, z1)-->t1, s3---fail(zone, false)-->s3},   {---:hb_B-->},
+       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
+         /\((tick(z, t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
+         /\((fail(zone, false))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
+         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
+         /\(z1:sva_SV0:1:1=
+         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
+       {t := t+1, z := z1}
     OT10 ------------------------------------------------------------
-        <t1_s3>-----:ra:1:1----><t1_s3>
+        <t1_s3>-----alpha0----><t1_s3>
 
 INFO  BIPArchFailureTimerMax_LTF3 -
-   {t1---cancel(false)-->t1, s3---resume(false)-->s3},   {---:hb_B:17:3-->},
-   [((cancel(false)=:ra:15:1))/\((:ra:15:1=cancel(b1:sva_SV1:1:2)))
-     /\((resume(false)=:ra:16:1))/\((:ra:16:1=resume(b2:sva_SV1:1:2)))
-     /\((:hb_B:17:3=resume))/\((b1:sva_SV1:1:2=b2:sva_SV1:1:2))/\((alpha1=:ra:1:2))],   {}
+       {t1---cancel(false)-->t1, s3---resume(false)-->s3},   {---:hb_B-->},
+       [(:hb_B=resume)/\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
+         /\((resume(false))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],   {}
     OT11 ------------------------------------------------------------
-        <t1_s3>-----:ra:1:2----><t1_s3>
+        <t1_s3>-----alpha1----><t1_s3>
 
 INFO  BIPArchFailureTimerMax_LTF3 -
-   {s3---reset-->s1},   {---:hb_E:116:8-->},
-   [((reset=:ra:114:1))/\((:ra:114:1=reset))/\((:hb_E:116:8=reset))/\((alpha3=:ra:1:4))],   {}
-    OT12 ------------------------------------------------------------
-        <t1_s3>-----:ra:1:4----><t1_s1>
+        {s3---reset-->s1},   {---:hb_E-->},     [(:hb_E=ask)],   {}
+    OT12 ------------------------------------------------------
+        <t1_s3>-----alpha3----><t1_s1>
 

### 2019-01-18 2018-Arch-pNets/arch-pNets.tex
Added OA duTimer simplifie
(minor) intro of pnets

--- 2019-01-18 2018-Arch-pNets/arch-pNets.tex
@@
 \label{secn:pNets}
+This section briefly describes pNets, see~\cite{HMZ-FORTE2016} for a  description of open pNets and their properties.
 \todoLHin{rewrite after uniformisation}
@@
 used to characterise a state, as part of actions, guards, and
-assignments. Without loss of generality and to simplify the formalisation, we suppose 
+assignments. 
+Without loss of generality and to simplify the formalisation, we suppose 
 here that 

### 2019-01-18 2018-Arch-pNets/arch-pNets.tex
Shorter pnet decription

--- 2019-01-18 2018-Arch-pNets/arch-pNets.tex
@@
 used to characterise a state, as part of actions, guards, and
-assignments. Without loss of generality and to simplify the formalisation, we suppose 
-here that 
-variables are local to each 
-state: each state has its set of variables disjoint from the others. Transmitting 
-variable values from one state to the other can be done by explicit assignment. 
+assignments. 
+%Without loss of generality and to simplify the formalisation, we suppose 
+%here that 
+%variables are local to each 
+%state: each state has its set of variables disjoint from the others. Transmitting 
+%variable values from one state to the other can be done by explicit assignment. 
 %Similarly, to simplify the management of variables and without loss of expressivity, we 
 %suppose that transitions looping to the same state does not do assignments.
-Note that we make no assumption on the finiteness of the set of states, nor
-on the finite branching of the transition relation.
-
-We first define the set of actions a pLTS can use, let $a$
-range over action labels. Action terms are  of the form $\alpha=a((?x_i)^{i \in I}, 
-\Expr_j^{j \in J})$, where $(?x_i)^{i \in I}$ are input variables, $\Expr_j^{j \in J})$ 
+%Note that we make no assumption on the finiteness of the set of states, nor
+%on the finite branching of the transition relation.
+We first define the set of actions a pLTS can use ($a$
+ranges over action labels):\\
+%. Action terms are  of the form 
+$\alpha=a(?x_i^{i \in I}, 
+\Expr_j^{j \in J})$, where $?x_i^{i \in I}$ are input variables, $\Expr_j^{j \in J}$ 
 are expressions.
@@
 		\vars(\dom(u))\!\in\!\vars(s')$. %,  and $s= s'\Rightarrow J=\emptyset$. 
-
-\end{itemize}
-\end{definition}
 \noteLH{is dom and codom clear?}
@@
 Will be solved if we roll back to \mbox{$(?x_i := e_i)^{i \in I}$} or \mbox{$\overline{?x := e}$}.}
-Now we define
-pNet nodes, as constructors for hierarchical behavioural structures.
+\noteLH{COORDINATION: I believe we should remove the constraints}		
+\end{itemize}
+\end{definition}
+%Now we define
+%pNets as constructors for hierarchical behavioural structures.
 A pNet has a set of sub-pNets that can be either pNets or pLTSs, and a
 set of holes, playing the role of process parameters.
-
-A composite pNet consists of a set of sub-pNets exposing
-a set of actions, each of them synchronising actions in each of
-the sub-pNets. The synchronisation between global actions and
-internal actions is given by  \emph{synchronisation vectors}: a
-synchronisation vector synchronises one or several internal actions, and
-exposes a single resulting global action.
+A  pNet consists of a set of sub-pNets exposing
+a set of global actions, each of them resulting from the synchronisation of internal actions in some sub-pNets. The synchronisation between global actions and
+internal actions is given by  \emph{synchronisation vectors}.
 Actions involved at the pNet level (in the synchronisation vectors) do
-not have input variables, \ie they 
+not need to distinguish input variables, \ie they 
 have the form $a(\Expr_j^{j \in J})$.
@@
 
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=0.8\columnwidth]{FailureTimerOA}
+  \caption{The open Automaton of the Failure Monitor Architecture}
+  \label{schema:ArchFailure:BIP}
+\end{figure}
+
 12 open transitions... Comments on the predicates ???

### 2019-01-18 2018-Arch-pNets/arch-pNets.tex
nouvelel figure OA detaille en page 39
Open automaton

@@
 \renewcommand{\Post}{u}
-The semantics of open pNets will be defined  as an open automaton. An open
-automaton is an automaton where each transition composes the actions of several holes, 
+The semantics of an open pNets is expressed as an open automaton, i.e., an automaton where each transition composes the actions of several holes, 
 the transition occurs if some predicates hold, and can involve a 
-set of state modifications.
+ state modifications.
 %\TODO{adopt a uniform notation for open transitions, almost each instance has a 
@@
 
-\end{example}
-
 The first one, $OT_1$, corresponds to the simultaneous initialisation
@@
 $''tick, fail, fail''$, with the hole B performing action $fail$......
-
-It is important to understand the difference between the red dotted rule and a normal 
-inference rule. They correspond to two different logical levels.
- The open transition is itself a logical implication, but using a simple logic (with the 
- expressive power that is given to the predicate and necessary include logical 
+\end{example}
+
+It is important to understand that the red dotted rule expresses an implication but at a different logical level compared to  a normal 
+inference rule. 
+ The open transition is  a logical implication that uses a simple logic with the 
+ expressive power  given by the predicate algebra (it must include logical 
  propositions and equality). We differentiate classical (black) inference rules that use 
- an expressive logic and are paper rules from open transition rules that use a simpler 
- logic, 
- will be embedded into automata transitions, and could typically be handled in a 
- mechanical way.
+ an expressive (higher order) logic and are paper rules from open transition rules that use a simpler  logic,  define automata transitions, and could  be handled 
+ mechanically.
 
@@
 OTs simplifiees a la main:
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=\columnwidth]{TimerOADetailed}
+  \caption{The open Automaton of the Failure Monitor Architecture}
+  \label{schema:ArchFailure:BIP}
+\end{figure}
 

### 2019-01-18 2018-Arch-pNets/arch-pNets.tex
Started the case-study section on architecture composition + some clean-up, particularly in the properties (current Example 1)

--- 2019-01-18 2018-Arch-pNets/arch-pNets.tex
@@
 }
-\newcommand{\tuple}[2][\ensuremath{,\allowbreak}]{%  
+\newcommand{\tuplebase}[2][\ensuremath{,\allowbreak}]{%  
   \def\nextitem{\def\nextitem{#1}}% Separator
@@
 
+\newcommand{\tuple}[2][\ensuremath{,\allowbreak}]{%
+  \setTupleDelims[(]{)}%
+  \tuplebase[#1]{#2}%
+}
+
 \newcommand{\Tuple}[2][\ensuremath{,\allowbreak}]{%
   \setTupleDelims[\Big(]{\Big)}%
-  \tuple[#1]{#2}%
+  \tuplebase[#1]{#2}%
 }
@@
   \setTupleDelims[\mylangle]{\myrangle}%
-  \tuple[#1]{#2}%
+  \tuplebase[#1]{#2}%
+}
+
+\newcommand{\listset}[2][\ensuremath{,\allowbreak}]{%
+  \setTupleDelims[\{]{\}}%
+  \tuplebase[#1]{#2}%
 }
@@
 \newcommand{\AG}[1][\ ]{\ensuremath{\mathtt{AG}#1}}
-\newcommand{\AF}[1][\ ]{\ensuremath{\mathtt{FG}#1}}
+\newcommand{\AF}[1][\ ]{\ensuremath{\mathtt{AF}#1}}
 \newcommand{\EF}[1][\ ]{\ensuremath{\mathtt{EF}#1}}
@@
   \label{defn:component}
-  A \emph{component} is a tuple $(Q, q^0, V, \val{0}{}, P,
-  \export, \goesto{})$, where
+  A \emph{component} is a tuple $\tuple{Q, q^0, V, \val{0}{}, P,
+  \export, \goesto{}}$, where
   \begin{itemize}
@@
       \label{eq:prop:z:top}
-      \AW[\quad]{(z = T)}{\PortFail} \land\quad
+      \AW[\quad]{(z = \topinterval)}{\PortFail} \land\quad
       \AG \bigl(
-      \PortReset \rightarrow \AW[]{(z = T)}{\PortFail}
+      \PortReset \rightarrow \AW[]{(z = \topinterval)}{\PortFail}
       \bigr).
@@
 assignments. 
-%Without loss of generality and to simplify the formalisation, we suppose 
-%here that 
-%variables are local to each 
-%state: each state has its set of variables disjoint from the others. Transmitting 
-%variable values from one state to the other can be done by explicit assignment. 
+Without loss of generality and to simplify the formalisation, we suppose 
+here that 
+variables are local to each 
+state: each state has its set of variables disjoint from the others. Transmitting 
+variable values from one state to the other can be done by explicit assignment. 
 %Similarly, to simplify the management of variables and without loss of expressivity, we 
 %suppose that transitions looping to the same state does not do assignments.
-%Note that we make no assumption on the finiteness of the set of states, nor
-%on the finite branching of the transition relation.
-We first define the set of actions a pLTS can use ($a$
-ranges over action labels):\\
-%. Action terms are  of the form 
-$\alpha=a(?x_i^{i \in I}, 
-\Expr_j^{j \in J})$, where $?x_i^{i \in I}$ are input variables, $\Expr_j^{j \in J}$ 
+Note that we make no assumption on the finiteness of the set of states, nor
+on the finite branching of the transition relation.
+
+We first define the set of actions a pLTS can use, let $a$
+range over action labels. Action terms are  of the form $\alpha=a((?x_i)^{i \in I}, 
+\Expr_j^{j \in J})$, where $(?x_i)^{i \in I}$ are input variables, $\Expr_j^{j \in J})$ 
 are expressions.
@@
 		\vars(\dom(u))\!\in\!\vars(s')$. %,  and $s= s'\Rightarrow J=\emptyset$.
+
+\end{itemize}
+\end{definition}
 \noteLH{is dom and codom clear?}
@@
 Will be solved if we roll back to \mbox{$(?x_i := e_i)^{i \in I}$} or \mbox{$\overline{?x := e}$}.}
-\noteLH{COORDINATION: I believe we should remove the constraints}		
-\end{itemize}
-\end{definition}
-%Now we define
-%pNets as constructors for hierarchical behavioural structures.
+Now we define
+pNet nodes, as constructors for hierarchical behavioural structures.
 A pNet has a set of sub-pNets that can be either pNets or pLTSs, and a
 set of holes, playing the role of process parameters.
-A  pNet consists of a set of sub-pNets exposing
-a set of global actions, each of them resulting from the synchronisation of internal actions in some sub-pNets. The synchronisation between global actions and
-internal actions is given by  \emph{synchronisation vectors}.
+
+A composite pNet consists of a set of sub-pNets exposing
+a set of actions, each of them synchronising actions in each of
+the sub-pNets. The synchronisation between global actions and
+internal actions is given by  \emph{synchronisation vectors}: a
+synchronisation vector synchronises one or several internal actions, and
+exposes a single resulting global action.
 Actions involved at the pNet level (in the synchronisation vectors) do
-not need to distinguish input variables, \ie they 
+not have input variables, \ie they 
 have the form $a(\Expr_j^{j \in J})$.
@@
 
+We now consider a system comprising two components $B_1$ and $B_2$
+with the corresponding interfaces $\tuple{V_i, P_i,
+  \export[i]}_{i=1,2}$, such that $\listset{\PortFail_i,
+  \PortResume_i} \subseteq P_i$, for $i = 1,2$.
+
+Assuming that the associated system requirements comprise the
+capability of monitoring the failure events corresponding to ports
+$\PortFail_1$ and $\PortFail_2$ of the two components, we would like
+to apply two instances of the Failure Monitor architecture.  However,
+we impose an additional constraint: only one timer coordinator is
+allowed, for example because it must eventually be implemented by a
+hardware component.
+
+We consider two architecture instances $A_i = \tuple{\cC_i, V_{A_i},
+  P_{A_i}, \export[A_i], \Gamma_i}$, for $i = 1,2$, with all their
+constituting elements cloned from the Failure Monitor architecture of
+the previous examples while substituting each entity $X$ by $X^i$.
+For instance, the initialisation of the $\mathit{zone}$ variable is
+transformed into $\IntervalInit[1]$ and $\IntervalInit[2]$,
+respectively.  The only exception to this cloning procedure are the
+sets of coordinating components: $\cC^i = \listset{\NameTimer,
+  \NameCtrl^i}$, \ie the $\NameTimer$ component is shared, while
+components $\NameCtrl^1$ and $\NameCtrl^2$ are obtained by making two
+copies of $\NameCtrl$ as above.
+
+In order to apply both architectures, we must verify that they are
+upwards compatible and compute the combined interaction model $\Gamma$
+in $A_1 \arcomp A_2 = \tuple{\cC_1 \cup \cC_2, V_{A_1} \cup V_{A_2},
+  P_{A_1} \cup P_{A_2}, \export[A_1] \cup \export[A_2], \Gamma}$
+(see \defn{arch:composition}).
+
 %****************************************************************

### 2019-01-18 2018-Arch-pNets/arch-pNets.tex
shorter affiliation
change les alpha en nom des dandling ports un peu partout... nouveau dessin de l'automate resultat en section 7.

--- 2019-01-18 2018-Arch-pNets/arch-pNets.tex
@@
 \renewcommand{\Post}{u}
-The semantics of an open pNets is expressed as an open automaton, i.e., an automaton where each transition composes the actions of several holes, 
+The semantics of open pNets will be defined  as an open automaton. An open
+automaton is an automaton where each transition composes the actions of several holes, 
 the transition occurs if some predicates hold, and can involve a 
- state modifications.
+set of state modifications.
 %\TODO{adopt a uniform notation for open transitions, almost each instance has a 
@@
 \begin{example}\emph{An open-transition.}
-  \label{OT:enable-composed}
-  \todoEM{Commenter...
-  Questions: les $\alpha$ n'apparaissent pas dans l'archi Bip; la
-  synchro des initialisations non plus... OT3 est un peu plus facile a
-  expliquer (;-).}
+  \label{Example:TimerOT3}
+
   The \texttt{Failure TimerMonitor} pNet of \Fig{FailureTimer:pNet} has 2 controllers 
-  and 2 holes. Two of its possible open-transitions are:
+  and 2 holes. One of its possible open-transitions is:
 
@@
 
- \smallskip
-$  OT_1  = \openrule
-{\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
-{\ostate{00} \OTarrow{\underline{\alpha_4}} \ostate{11}}
-$
+  %% Removed to save space:
+%%  \smallskip
+%% $  OT_1  = \openrule
+%% {\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
+%% {\ostate{00} \OTarrow{\underline{\alpha_4}} \ostate{11}}
+%% $
 \medskip
@@
     \{z:=z1\} }
-  {\ostate{11} \OTarrow{\underline{\alpha_0}} \ostate{12}}
+  %  {\ostate{11} \OTarrow{\underline{\alpha_0}} \ostate{12}}
+    {\ostate{11} \OTarrow{fail} \ostate{12}}
   $
+
+\end{example}
 
@@
 $''tick, fail, fail''$, with the hole B performing action $fail$......
-\end{example}
-
-It is important to understand that the red dotted rule expresses an implication but at a different logical level compared to  a normal 
-inference rule. 
- The open transition is  a logical implication that uses a simple logic with the 
- expressive power  given by the predicate algebra (it must include logical 
+
+It is important to understand the difference between the red dotted rule and a normal 
+inference rule. They correspond to two different logical levels.
+ The open transition is itself a logical implication, but using a simple logic (with the 
+ expressive power that is given to the predicate and necessary include logical 
  propositions and equality). We differentiate classical (black) inference rules that use 
- an expressive (higher order) logic and are paper rules from open transition rules that use a simpler  logic,  define automata transitions, and could  be handled 
- mechanically.
+ an expressive logic and are paper rules from open transition rules that use a simpler 
+ logic, 
+ will be embedded into automata transitions, and could typically be handled in a 
+ mechanical way.
 
@@
 
+%% \begin{figure}[t]
+%%   \centering
+%%   \includegraphics[width=\columnwidth]{TimerOpenAut}
+%%   \caption{The open Automaton of the Failure Monitor Architecture}
+%%   \label{schema:ArchFailure:BIP}
+%% \end{figure}
+
 \begin{figure}[t]
   \centering
-  \includegraphics[width=\columnwidth]{TimerOpenAut}
+  \includegraphics[width=\columnwidth]{TimerOADetailed}
   \caption{The open Automaton of the Failure Monitor Architecture}
-  \label{schema:ArchFailure:BIP}
+  \label{schema:ArchFailure:OA}
 \end{figure}
 
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=0.8\columnwidth]{FailureTimerOA}
-  \caption{The open Automaton of the Failure Monitor Architecture}
-  \label{schema:ArchFailure:BIP}
-\end{figure}
-
-12 open transitions... Comments on the predicates ???
-
-Should list some temporal logic properties....
+In Figure~\ref{schema:ArchFailure:OA} we show the full open automaton
+obtained from our pNet. For reasons of space, we have not shown the
+detail of the open transition, but only the assignement of state
+variables, and the resulting action. You can find the full details in
+Appendix \ref{secn:full-results}. As an example, $OT_3$ is the one explained in Example
+\ref{Example:TimerOT3} page \pageref{Example:TimerOT3}.
 
@@
 --------------------
-SV0 SVs: <tick(z, t, z1), fail(zone, b1), fail(b0), _>-->alpha0,
+SV0 SVs: <tick(z, t, z1), fail(zone, b1), fail(b0), _>-->fail,
                           [((b1->b0)/\(z1=z/\(((b1?(zone)TopInt)))+t)))]
-SV1 SVs: <cancel(b1), resume(b2), resume, _>-->alpha1, (b1=b2)
-SV2 SVs: <timeout, timeout, _, ask>-->alpha2
-SV3 SVs: <_, reset, _, reset>-->alpha3
-SV4 SVs: <init, init, _, _>-->alpha4
+SV1 SVs: <cancel(b1), resume(b2), resume, _>-->resume, (b1=b2)
+SV2 SVs: <timeout, timeout, _, ask>-->ask
+SV3 SVs: <_, reset, _, reset>-->reset
+SV4 SVs: <init, init, _, _>-->init
 pLTS: Timer
@@
     OT1 ------------------------------------------------------------
-        <t0_s0>-----alpha4----><t1_s1>
+        <t0_s0>-----init----><t1_s1>
 
@@
     OT2 ------------------------------------------------------------
-        <t1_s1>-----alpha0----><t1_s1>
+        <t1_s1>-----fail----><t1_s1>
 
@@
     OT3 ------------------------------------------------------------
-        <t1_s1>-----alpha0----><t1_s2>
+        <t1_s1>-----fail----><t1_s2>
 
@@
     OT4 ------------------------------------------------------------
-        <t1_s1>-----alpha1----><t1_s1>
+        <t1_s1>-----resume----><t1_s1>
 
@@
     OT5 ------------------------------------------------------------
-        <t1_s1>-----alpha2----><t1_s1>
+        <t1_s1>-----ask----><t1_s1>
 
@@
     OT6 ------------------------------------------------------------
-        <t1_s2>-----alpha0----><t1_s2>
+        <t1_s2>-----fail----><t1_s2>
 
@@
     OT7 ------------------------------------------------------------
-        <t1_s2>-----alpha1----><t1_s2>
+        <t1_s2>-----resume----><t1_s2>
 
@@
     OT8 ------------------------------------------------------------
-        <t1_s2>-----alpha1----><t1_s1>
+        <t1_s2>-----resume----><t1_s1>
 
@@
     OT9 ------------------------------------------------------------
-        <t1_s2>-----alpha2----><t1_s3>
+        <t1_s2>-----ask----><t1_s3>
 
@@
     OT10 ------------------------------------------------------------
-        <t1_s3>-----alpha0----><t1_s3>
+        <t1_s3>-----fail----><t1_s3>
 
@@
     OT11 ------------------------------------------------------------
-        <t1_s3>-----alpha1----><t1_s3>
+        <t1_s3>-----resume----><t1_s3>
 
@@
     OT12 ------------------------------------------------------
-        <t1_s3>-----alpha3----><t1_s1>
+        <t1_s3>-----reset----><t1_s1>
 
@@
 {\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
-{\ostate{00} \OTarrow{\underline{\alpha_4}} \ostate{11}}
+{\ostate{00} \OTarrow{init} \ostate{11}}
 $
@@
   \{z:=z1\} }
-{\ostate{11} \OTarrow{\underline{\alpha_0}} \ostate{11}}
+{\ostate{11} \OTarrow{fail} \ostate{11}}
 $
@@
     \{z:=z1\} }
-  {\ostate{11} \OTarrow{\underline{\alpha_0}} \ostate{12}}
+  {\ostate{11} \OTarrow{fail} \ostate{12}}
   $
@@
     \{\}  }
-  {\ostate{11} \OTarrow{\underline{\alpha_1}} \ostate{11}}
+  {\ostate{11} \OTarrow{resume} \ostate{11}}
   $
@@
     \{t:=t+1\}  }
-  {\ostate{11} \OTarrow{\underline{\alpha_2}} \ostate{11}}
+  {\ostate{11} \OTarrow{ask} \ostate{11}}
+  $
+  \medskip
+
+  $  OT_6  = \openrule
+  {\{B\mapsto fail(b0)\},\\
+    t<GetMax(z) \land b1=false \land b1=>b0 \land z1=(z \cap (b1?zone;TopInt)+t),
+    \{t:=t+1, z:=z1\} }
+  {\ostate{12} \OTarrow{fail} \ostate{12}}
   $
@@
     \{\} }
-  {\ostate{12} \OTarrow{\underline{\alpha_1}} \ostate{12}}
+  {\ostate{12} \OTarrow{resume} \ostate{12}}
   $
@@
     \{t:=0, z:=TopInt\} }
-  {\ostate{12} \OTarrow{\underline{\alpha_1}} \ostate{11}}
+  {\ostate{12} \OTarrow{resume} \ostate{11}}
   $
@@
     \{t:=t+1\} }
-  {\ostate{12} \OTarrow{\underline{\alpha_2}} \ostate{13}}
+  {\ostate{12} \OTarrow{ask} \ostate{13}}
   $
@@
     \{t:=t+1, z:=z1\} }
-  {\ostate{13} \OTarrow{\underline{\alpha_0}} \ostate{13}}
+  {\ostate{13} \OTarrow{fail} \ostate{13}}
   $
@@
     \{\} }
-  {\ostate{13} \OTarrow{\underline{\alpha_1}} \ostate{13}}
+  {\ostate{13} \OTarrow{resume} \ostate{13}}
   $
@@
     \{\} }
-  {\ostate{13} \OTarrow{\underline{\alpha_3}} \ostate{11}}
+  {\ostate{13} \OTarrow{reset} \ostate{11}}
   $

### 2019-01-18 2018-Arch-pNets/arch-pNets.tex

@@
   \and
-	Univ Lyon, CNRS, ENS de Lyon, Inria, Universit\'e Claude Bernard Lyon 1, LIP UMR 5668, Lyon, France\\\email{ludovic.henrio@ens-lyon.fr}
+	Univ Lyon, CNRS, ENS de Lyon, Inria, Universit\'e Claude Bernard Lyon 1, LIP, Lyon, France\\\email{ludovic.henrio@ens-lyon.fr}
   \and

### 2019-01-23 2018-Arch-pNets/arch-pNets.tex
pNets in 2.5 pages

--- 2019-01-18 2018-Arch-pNets/arch-pNets.tex
@@
   \and
-	Univ Lyon, CNRS, ENS de Lyon, Inria, Universit\'e Claude Bernard Lyon 1, LIP UMR 5668, Lyon, France\\\email{ludovic.henrio@ens-lyon.fr}
+	Univ Lyon, CNRS, ENS de Lyon, Inria, Universit\'e Claude Bernard Lyon 1, LIP, Lyon, France -- \email{ludovic.henrio@ens-lyon.fr}
   \and
@@
 \label{secn:pNets}
-This section briefly describes pNets, see~\cite{HMZ-FORTE2016} for a  description of open pNets and their properties.
-\todoLHin{rewrite after uniformisation}
+This section briefly describes pNets, see~\cite{HMZ-FORTE2016} for more complete   description.
 pNets are tree-like structures, where the leaves are either
@@
 behaviour of basic processes, or \emph{holes}, used as placeholders
-for unknown processes, of which we only specify the set of possible
-actions, this set is named the \emph{sort}.
-Nodes of the tree (pNet nodes) are synchronising artifacts, using a
+for unknown processes.
+Nodes of the tree are synchronising artefacts using a
 set of \emph{synchronisation vectors} that express the possible
@@
 
-\subsection{The (open) pNets Core Model}
+\paragraph{pNets definition.}
 \label{section:pNets}
-
-A pLTS is a labelled transition system with variables. Variables can be
+A pLTS is a labelled transition system with variables that can be
 used to characterise a state, as part of actions, guards, and
@@
 %on the finite branching of the transition relation.
-We first define the set of actions a pLTS can use ($a$
+We  define the set of actions a pLTS can use ($a$
 ranges over action labels):\\
@@
 \begin{itemize}
-\item[$\bullet$]
+\item
 $S$ is a set of states, $\vars(s)$ denotes the set of associated variables;
-\item[$\bullet$]
+\item
 $s_0 \in S$ is the initial state;
@@
 %by the additional assignments.
-\item[$\bullet$] $\to \subseteq S \times L \times S$ is the transition relation and 
+\item $\to \subseteq S \times L \times S$ is the transition relation and 
 $L$ is the set of labels of the form
@@
 assigns updated value for variables in the destination state. 
-If 
-$s \xrightarrow{\langle \alpha,~g,~u\rangle} s'\in \to $ then 
-% REMOVED BECAUSE USELESS: $\iv(\alpha)\!\subseteq\! \vars(s')$, 
-		$\vars(\alpha)\backslash \iv(\alpha)\!\subseteq\! \vars(s)$, 
-		$\vars(g)\!\subseteq\! \vars(s)\cup\vars(\alpha)$, and
-		$\vars(\codom(u))\!\subseteq\! \vars(s)\cup\vars(\alpha)\land 
-		\vars(\dom(u))\!\in\!\vars(s')$. %,  and $s= s'\Rightarrow J=\emptyset$. 
-\noteLH{is dom and codom clear?}
-\noteSB{Not sure: I understand, because I know what is meant, but this is not a canonical use, so should be explained.
+%%% SHORTEN BY LUDO
+%If 
+%$s \xrightarrow{\langle \alpha,~g,~u\rangle} s'\in \to $ then 
+%% REMOVED BECAUSE USELESS: $\iv(\alpha)\!\subseteq\! \vars(s')$, 
+%		$\vars(\alpha)\backslash \iv(\alpha)\!\subseteq\! \vars(s)$, 
+%		$\vars(g)\!\subseteq\! \vars(s)\cup\vars(\alpha)$, and
+%		$\vars(\codom(u))\!\subseteq\! \vars(s)\cup\vars(\alpha)\land 
+%		\vars(\dom(u))\!\in\!\vars(s')$. %,  and $s= s'\Rightarrow J=\emptyset$. 
+%\noteLH{is dom and codom clear?}
+%\noteSB{Not sure: I understand, because I know what is meant, but this is not a canonical use, so should be explained.
 Will be solved if we roll back to \mbox{$(?x_i := e_i)^{i \in I}$} or \mbox{$\overline{?x := e}$}.}
-\noteLH{COORDINATION: I believe we should remove the constraints}		
+%\noteLH{COORDINATION: I believe we should remove the constraints}		
 \end{itemize}
@@
 %pNets as constructors for hierarchical behavioural structures.
-A pNet has a set of sub-pNets that can be either pNets or pLTSs, and a
-set of holes, playing the role of process parameters.
-A  pNet consists of a set of sub-pNets exposing
-a set of global actions, each of them resulting from the synchronisation of internal actions in some sub-pNets. The synchronisation between global actions and
-internal actions is given by  \emph{synchronisation vectors}.
-Actions involved at the pNet level (in the synchronisation vectors) do
+A pNet composes several pNets, pLTSs, and holes playing the role of process parameters.
+A  pNet  exposes
+ global actions resulting from the synchronisation of internal actions in some sub-pNets. 
+This synchronisation  is specified by  \emph{synchronisation vectors}.
+Actions involved in the synchronisation vectors do
 not need to distinguish input variables, \ie they 
@@
 \begin{definition}[pNets]\label{defn:pnets}
-A pNet is a hierarchical structure where leaves are pLTSs and holes\footnote{Typing can 
-be added to pNets by defining and checking their interfaces, called 
-sort~\cite{HMZ-FORTE2016}}:
+A pNet is a hierarchical structure where leaves are pLTSs and holes: %\footnote{Typing can 
+%be added to pNets by defining and checking their interfaces, called 
+%sort~\cite{HMZ-FORTE2016}}:
 $\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, J, \symb{SV}_k^{k\in 
@@
 \begin{itemize}
-\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets;
+\item $\pNet_i^{i\in I}$ is the family of sub-pNets;
 %  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which 
@@
 
-\item[$\bullet$] $J$ is a set of indexes, called \emph{holes}.
+\item $J$ is a set of indexes, called \emph{holes}.
 $I$ and $J$ are \emph{disjoint}: $I\!\cap\! J=\emptyset$,  $I\!\cup\! J\neq\emptyset$
@@
 
-\item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
+\item $\symb{SV}_k^{k\in K}$ is a set of
   synchronisation vectors. % (\hl{$K\in\I_\P$}). 
@@
 \end{itemize}
-We define the set of holes and leaves of a pNet as follows:
-  \begin{itemize}
-\item
-The set of holes $\Holes(\pNet_{i_1})$ of a pNet is the indexes of the holes of the pNet 
+%We define the set of holes and leaves of a pNet as follows:
+%  \begin{itemize}
+%\item
+The set of \emph{holes} $\Holes(\pNet_{i_1})$ of a pNet is the indexes of the holes of the pNet 
 itself plus the indexes of all the holes of its subnets (we suppose those indexes 
-disjoints).
+disjoints). A pNet $Q$ is \emph{closed} if it has no hole: $\Holes(Q)=\emptyset$; else it
+is said to be \emph{open}.
 %
@@
 %\end{array}\]
-\item
-The set of leaves of a pNet is the set of all pLTSs occurring in the structure, as an 
+%\item
+The set of \emph{leaves} of a pNet is the set of all pLTSs occurring in the structure, as an 
 indexed family of the form $\Leaves(\pNet)= \mylangle \pNet_i \myrangle^{i \in L}$.
-is said to be \emph{open}.
-\end{itemize}
-A pNet $Q$ is \emph{closed} if it has no hole: $\Holes(Q)=\emptyset$; else it
-is said to be \emph{open}.
+%\end{itemize}
+
 \end{definition}
 
-\subsection{Operational Semantics for Open pNets}
+\paragraph{Operational Semantics for Open pNets.}
 \label{section:op-semantics}
@@
 	a structure of the form:
+\\[-2ex]	
 	\begin{mathpar}
@@
 
+The red dotted rule expresses an implication but at a different logical level compared to  a normal 
+inference rule. 
+ The open transition is  a logical implication that uses a simple logic with the 
+ expressive power  given by the predicate algebra (it must include logical 
+ propositions and equality). We differentiate classical (black) inference rules that use 
+ an expressive (higher order) logic and are paper rules from open transition rules that use a simpler  logic,  define automata transitions, and could  be handled 
+ mechanically.
+
+\begin{definition}[Open automaton]
+	\label{defn:open-automaton}
+	An \emph{open automaton} is a structure\\ $A =
+	<J,\mathcal{S},s_0,\mathcal{T}>$ where:
+	\begin{itemize}
+		\item   $J$ is a  set of indices,
+		\item   $\mathcal{S}$ is a set of states and $s_0$ an initial state
+		among $\mathcal{S}$,
+		\item $\mathcal{T}$ is a set of open transitions and for each
+		$t\in \mathcal{T}$ there exist  $J'$ with  $J'
+		\subseteq J$, such that $t$ is an open transition over  $J'$,
+		and  $\mathcal{S}$.
+
+	\end{itemize}
+\end{definition}
+
+%
+%Then the semantics of a pNet is characterized by a set of {\em open
+%transitions}, where the hypotheses on process parameters are
+%replaced by 1) transitions of the pLTSs at the leaves, and 2) formal
+%hypotheses on the transitions of the holes. A {\em predicate} is used
+%to relate the parameters and names appearing in the actions of the
+%leaves and the holes involved in the rules, but also appearing in  the resulting action.
+
+We build the semantics of open pNets as an open automaton where  the states are
+tuples of states of the pLTSs at the leaves. We denote them $\triangleleft\ldots\triangleright$ for distinguishing tuple 
+states from other tuples. given by 
+Definition~\ref{def-states}. 
+The open transitions first
+ project the global state into states of the leaves, then apply
+pLTS transitions on these states, and compose them with the sort of the holes according to the synchronisation defined in the synchronisation vectors.
+More precisely, each open transition between two states is defined as a composition of transition from some pLTSs and actions of some holes as follows: 1) the actions of the holes involved in the transition, 2) a guard  built from the synchronisation vectors coordinating the holes and the transitions involved; 3) assignments defined by the pLTSs transitions involved.
+The synchronisation vectors also define the global action.
+The global state evolution is also defined by the set of state transitions of the pLTSs involved in the pLTSs.
+
 \begin{example}\emph{An open-transition.}
   \label{OT:enable-composed}
-  \todoEM{Commenter...
-  Questions: les $\alpha$ n'apparaissent pas dans l'archi Bip; la
-  synchro des initialisations non plus... OT3 est un peu plus facile a
-  expliquer (;-).}
   The \texttt{Failure TimerMonitor} pNet of \Fig{FailureTimer:pNet} has 2 controllers 
-  and 2 holes. Two of its possible open-transitions are:
-
+  and 2 holes. One of its possible open-transitions is:\\[-2ex]
 %%   \footnote{Note the underlined action notation that we use to represent synchronised actions, i.e.
@@
 %% \noteLH{underline notation might be a bit too much for this paper : see at the end if we remove it or not (will we use it?)}
-
- \smallskip
-$  OT_1  = \openrule
-{\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
-{\ostate{00} \OTarrow{\underline{\alpha_4}} \ostate{11}}
-$
-\medskip
-
-  $  OT_3  = \openrule
+% \smallskip
+%$  OT_1  = \openrule
+%{\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
+%{\ostate{00} \OTarrow{\underline{\alpha_4}} \ostate{11}}
+%$
+%\medskip
+\begin{small}\[ \openrule
   {\{B\mapsto fail(b0)\},\\
@@
     \{z:=z1\} }
-  {\ostate{11} \OTarrow{\underline{\alpha_0}} \ostate{12}}
-  $
-
-The first one, $OT_1$, corresponds to the simultaneous initialisation
-of both controlers. No hole is active at that time, and the resulting
-global action is denoted $\alpha_4$.
-
-The second one, $OT_3$, correspond to the firing of the connector
-$''tick, fail, fail''$, with the hole B performing action $fail$......
+  {\ostate{11} \OTarrow{\alpha_0} \ostate{12}}
+  \]
+\end{small}\vspace{-1.5ex}
+%
+%The first one, $OT_1$, corresponds to the simultaneous initialisation
+%of both controlers. No hole is active at that time, and the resulting
+%global action is denoted $\alpha_4$.
+
+It correspond to the firing of the connector
+$''tick, fail, fail''$.
+It states that, if the hole B performs an action $fail$, and the (complex) guard is satisfied, then the variable $z$ is set to $z1$ (as specified by the guard), then the transition below the dotted line occurs and a global action labelled $\alpha_0$ occurs.
+Only the second pLTS performs a transition from state $1$ to state $2$.
+The guard corresponds both to the guard of this transition and to synchronisation vector constraints.
 \end{example}
-
-It is important to understand that the red dotted rule expresses an implication but at a different logical level compared to  a normal 
-inference rule. 
- The open transition is  a logical implication that uses a simple logic with the 
- expressive power  given by the predicate algebra (it must include logical 
- propositions and equality). We differentiate classical (black) inference rules that use 
- an expressive (higher order) logic and are paper rules from open transition rules that use a simpler  logic,  define automata transitions, and could  be handled 
- mechanically.
-
-\begin{definition}[Open automaton]
-	\label{defn:open-automaton}
-	An \emph{open automaton} is a structure\\ $A =
-	<J,\mathcal{S},s_0,\mathcal{T}>$ where:
-	\begin{itemize}
-		\item[$\bullet$]   $J$ is a  set of indices,
-		\item[$\bullet$]   $\mathcal{S}$ is a set of states and $s_0$ an initial state
-		among $\mathcal{S}$,
-		\item[$\bullet$] $\mathcal{T}$ is a set of open transitions and for each
-		$t\in \mathcal{T}$ there exist  $J'$ with  $J'
-		\subseteq J$, such that $t$ is an open transition over  $J'$,
-		and  $\mathcal{S}$.
-
-	\end{itemize}
-\end{definition}
-
-%
-%Then the semantics of a pNet is characterized by a set of {\em open
-%transitions}, where the hypotheses on process parameters are
-%replaced by 1) transitions of the pLTSs at the leaves, and 2) formal
-%hypotheses on the transitions of the holes. A {\em predicate} is used
-%to relate the parameters and names appearing in the actions of the
-%leaves and the holes involved in the rules, but also appearing in  the resulting action.
-
-We define states of open pNets as tuples of states, where we denote tuples
-in structured states as $\triangleleft\ldots\triangleright$ for distinguishing tuple 
-states from other tuples.
-\begin{definition}[States of open pNets]\label{def-states}
-  A state of an open pNet is a tuple (not necessarily finite) of the
-  states of its leaves.
-
-  For any pNet p, let $\Leaves(p) = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be 
-  the set of pLTS at its leaves,
-  then $States(p) = \{\triangleleft s_i^{i\in L}
-  \triangleright| \forall i\in L. s_i \in S_i\}$.
-A pLTS being its own single leave:
-  $States(\mylangle S,s_0, \to\myrangle) = \{\triangleleft s \triangleright| s \in S\}$.
-
-The initial state is defined as:
-$InitState(p) = \triangleleft {{s_i}_0}^{i\in L}  \triangleright$.
-\end{definition}
-
-%% \begin{example} \emph{State of a pNet}
-%%   The states of pNet \texttt{EnableCompL} are:
-%%   $\triangleleft 00 \triangleright, \triangleleft 10 \triangleright, \triangleleft 11 
-%%\triangleright$
-%% \end{example}
-
-\paragraph{Predicates:}
-Let
-$\mylangle\overline{\pNet},\overline{\Sort},\overline{\symb{SV}}\myrangle$
-be a pNet. Consider a synchronisation vector $\symb{SV}\in \overline{\symb{SV}}$. We 
-define a
-predicate $\Pred$ relating
-the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
-\begin{multline}
-\Predsv(\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
-{\alpha'} {g}, \alpha_i^{i\in I}, \beta_j^{j\in J}, \alpha)\Leftrightarrow \\
-\forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, \beta_j=\beta'_j \land 
-\alpha=\alpha' 
-\land g
-\end{multline}
-
-Somehow, this predicate entails a verification of satisfiability in the sense that if the 
-predicate $\Pred_{\symb{sv}}$ is not satisfiable, then the transition associated with the 
-synchronisation will not occur in the considered state.
-
-In any other case (if the action families do not match or if there is no valuation of
-variables such that the above formula can be ensured) the predicate is undefined.
-
-This definition is not constructive but it is easy to build the predicate constructively
-by brute-force unification of the sub-pNets
-actions with the corresponding vector actions, possibly followed by a simplification
-step.
-
-We build the semantics of open pNets as an open automaton where LTSs are the pLTSs at
-the leaves of the pNet structure, and the states are given by 
-Definition~\ref{def-states}. The open transitions first
- project the global state into states of the leaves, then apply
-pLTS transitions on these states, and compose them with the sort of the holes. %The pNet
-%structure does not appear in the open-automaton, only the
-%set of Holes and the set of Leaves.
-The semantics    instantiates \emph{fresh} variables, additionally, for an action 
-$\alpha$, $\fresh(\alpha)$ means all variables in $\alpha$ are fresh.
-
-\begin{definition}[Operational semantics of open pNets]
-	\label{defn:operationalSemantics}
-	The semantics of a pNet $p$ is an open automaton $A = 
-	<Holes(p),States(p),InitState(p),
-	\mathcal{T}>$ where $\mathcal{T}$ is the smallest set of open transitions		
-	satisfying the rules below:
-%	\begin{itemize}
-%		\item $J$ is the set of holes: $Holes(p)= J$. 
-		%  \item $\overline{L}^L = Leaves(p), \overline{H}^J = Holes(p)$
-%		\item ${\mathcal{S}} = States(p)$ and $s_0 = InitState(p)$
-%		\item $\mathcal{T}$ is the smallest set of open transitions		satisfying the 
-%rules below:
-%	\end{itemize}
-
-	%% \TODO{ We should be careful here: after (re) reading "Huimin
-	%% 	Lin, 'Symbolic Transition Systems with Assignements', Concur'96" I
-	%% 	think handling assignments is not trivial, even for comparisons of pLTSs. }
-
-	The rule for a pLTS  checks that the guard 
-	is verified and transforms assignments into post-conditions:
-
-	\begin{description}
-		\item[{\bf Tr1:}]
-	$\inferrule
-		{ s \xrightarrow{\langle \alpha,~g,~u\rangle} s'\in \to  }
-		{ \mylangle  S,s_0, \to \myrangle
-			\models
-			\openrule
-			{\emptyset ,
-			g,u}
-			{\ostate{s} \OTarrow{\alpha} \ostate{s'}}
-		}
-		$
-	\end{description}
-%	Note that this note is greatly simplified by the fact that variables are local to 
-%	thread; introducing global state variables or accepting loops to the same 
-%	state would 
-%	require to reason 
-%	on the scope of 
-%	each variables, and to introduce additional variables to handle the several occurence 
-%	of the same pLTS variable in the predicates. Indeed the constraints on pLTS 
-%	transitions 
-%	ensure that the same variable never appears both on the left and on the right of the 
-%	equations of a predicate.
-
-	The second rule deals with pNet nodes: for each possible
-	synchronisation vector (of index $k$) applicable to the rule subject, the premisses
-	include one {\em open transition} for each sub-pNet involved , one possible
-	{\em action} for each Hole involved, and the predicate relating these
-	with the resulting action of the vector. The sub-pNets involved are split between two 
-	sets, $I_2$ for subnets that are pLTSs, and $I_1$ for the others, $J$ is the set of 
-	holes involved in the transition\footnote{Formally, if $SV_k \!=\! \SV{\alpha_m^{m 
-	\in M}}{\alpha'}{g}$ is a synchronisation vector  of \pNet\  then $J=M\cap 
-	\Holes(\pNet)$, $I_2=M\cap \Leaves(\pNet)$,  $I_1=M\setminus J \setminus 
-	I_2$}.
-
-	\begin{description}
-		\item[{\bf Tr2:}]
-	\end{description}
-
+%
+%\begin{definition}[States of open pNets]\label{def-states}
+%  A state of an open pNet is a tuple (not necessarily finite) of the
+%  states of its leaves.
+%
+%  For any pNet p, let $\Leaves(p) = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be 
+%  the set of pLTS at its leaves,
+%  then $States(p) = \{\triangleleft s_i^{i\in L}
+%  \triangleright| \forall i\in L. s_i \in S_i\}$.
+%A pLTS being its own single leave:
+%  $States(\mylangle S,s_0, \to\myrangle) = \{\triangleleft s \triangleright| s \in S\}$.
+%
+%The initial state is defined as:
+%$InitState(p) = \triangleleft {{s_i}_0}^{i\in L}  \triangleright$.
+%\end{definition}
+%
+%
+%
+%%% \begin{example} \emph{State of a pNet}
+%%%   The states of pNet \texttt{EnableCompL} are:
+%%%   $\triangleleft 00 \triangleright, \triangleleft 10 \triangleright, \triangleleft 11 
+%%%\triangleright$
+%%% \end{example}
+%
+%\paragraph{Predicates:}
+%Let
+%$\mylangle\overline{\pNet},\overline{\Sort},\overline{\symb{SV}}\myrangle$
+%be a pNet. Consider a synchronisation vector $\symb{SV}\in \overline{\symb{SV}}$. We 
+%define a
+%predicate $\Pred$ relating
+%the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
+%\begin{multline}
+%\Predsv(\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
+%{\alpha'} {g}, \alpha_i^{i\in I}, \beta_j^{j\in J}, \alpha)\Leftrightarrow \\
+%\forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, \beta_j=\beta'_j \land 
+%\alpha=\alpha' 
+%\land g
+%\end{multline}
+%
+%
+% 
+%
+%Somehow, this predicate entails a verification of satisfiability in the sense that if the 
+%predicate $\Pred_{\symb{sv}}$ is not satisfiable, then the transition associated with the 
+%synchronisation will not occur in the considered state. 
+%
+%
+%In any other case (if the action families do not match or if there is no valuation of
+%variables such that the above formula can be ensured) the predicate is undefined.
+%
+%This definition is not constructive but it is easy to build the predicate constructively
+%by brute-force unification of the sub-pNets
+%actions with the corresponding vector actions, possibly followed by a simplification
+%step.
+%
+%
+%
+%
+%\begin{definition}[Operational semantics of open pNets]
+%	\label{defn:operationalSemantics}
+%	The semantics of a pNet $p$ is an open automaton $A = 
+%	<Holes(p),States(p),InitState(p),
+%	\mathcal{T}>$ where $\mathcal{T}$ is the smallest set of open transitions		
+%	satisfying the rules below:
+%%	\begin{itemize}
+%%		\item $J$ is the set of holes: $Holes(p)= J$. 
+%		%  \item $\overline{L}^L = Leaves(p), \overline{H}^J = Holes(p)$
+%%		\item ${\mathcal{S}} = States(p)$ and $s_0 = InitState(p)$
+%%		\item $\mathcal{T}$ is the smallest set of open transitions		satisfying the 
+%%rules below:
+%%	\end{itemize}
+%	
+%	%% \TODO{ We should be careful here: after (re) reading "Huimin
+%	%% 	Lin, 'Symbolic Transition Systems with Assignements', Concur'96" I
+%	%% 	think handling assignments is not trivial, even for comparisons of pLTSs. }
+%
+%
+%	
+%	The rule for a pLTS  checks that the guard 
+%	is verified and transforms assignments into post-conditions:
+%	
+%	\begin{description}
+%		\item[{\bf Tr1:}]
+%	$\inferrule
+%		{ s \xrightarrow{\langle \alpha,~g,~u\rangle} s'\in \to  }
+%		{ \mylangle  S,s_0, \to \myrangle
+%			\models
+%			\openrule
+%			{\emptyset ,
+%			g,u}
+%			{\ostate{s} \OTarrow{\alpha} \ostate{s'}}
+%		}
+%		$
+%	\end{description}
+%%	Note that this note is greatly simplified by the fact that variables are local to 
+%%	thread; introducing global state variables or accepting loops to the same 
+%%	state would 
+%%	require to reason 
+%%	on the scope of 
+%%	each variables, and to introduce additional variables to handle the several occurence 
+%%	of the same pLTS variable in the predicates. Indeed the constraints on pLTS 
+%%	transitions 
+%%	ensure that the same variable never appears both on the left and on the right of the 
+%%	equations of a predicate.
+%	
+%	The second rule deals with pNet nodes: for each possible
+%	synchronisation vector (of index $k$) applicable to the rule subject, the premisses
+%	include one {\em open transition} for each sub-pNet involved , one possible
+%	{\em action} for each Hole involved, and the predicate relating these
+%	with the resulting action of the vector. The sub-pNets involved are split between two 
+%	sets, $I_2$ for subnets that are pLTSs, and $I_1$ for the others, $J$ is the set of 
+%	holes involved in the transition\footnote{Formally, if $SV_k \!=\! \SV{\alpha_m^{m 
+%	\in M}}{\alpha'}{g}$ is a synchronisation vector  of \pNet\  then $J=M\cap 
+%	\Holes(\pNet)$, $I_2=M\cap \Leaves(\pNet)$,  $I_1=M\setminus J \setminus 
+%	I_2$}.                                                                    
+%	           
+%	                                                       
+%	\begin{description}
+%		\item[{\bf Tr2:}]
+%	\end{description}
+%	
+%%	\noindent
+%%\begin{mathpar}
+%%    \mprset {vskip=1ex}
+%%\inferrule
+%%    {
+%%\Leaves(\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in 
+%%    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
+%%k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{g} 
+%%\\
+%%\\     	
+%%	\forall m\!\!\in\!\! I_1. {\pNet_m 
+%%	\models\openrule
+%%    	{
+%%    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
+%%    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
+%%    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
+%%  \qquad
+%%\forall m\!\!\in\!\! I_2.		{ \pNet_m 
+%%    	 \models
+%%    	\openrule
+%%    	{\emptyset, \Pred_m, \Post_m}
+%%    	{\ostate{s_m} \OTarrow {\alpha_m}
+%%    		\ostate{s_m'}} }\\\\
+%%     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
+%%    	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
+%%    	\Pred_{\symb{sv}}(SV_k,\alpha_m^{m\in (I_1\uplus I_2)},\beta_j^{j\in J},\alpha)\\ 
+%%    		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
+%%    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
+%%    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
+%%    }
+%%    {\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
+%%    	\models
+%%    	{\openrule
+%%    		{
+%%    		{\beta_j}^{j\in J^\prime}, \Pred, \uplus_{m\in I_1\uplus I_2} 
+%%    		\Post_m}
+%%    		{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
+%%    			\ostate{(s_i^\prime)^{i\in L}}}
+%%    	}
+%%    }
+%%\end{mathpar}  
 %	\noindent
 %\begin{mathpar}
-%    \mprset {vskip=1ex}
+%    \mprset {vskip=.8ex}
 %\inferrule
 %    {
-%\Leaves(\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in 
+%\Leaves(\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in 
 %    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
-%k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{g} 
+%k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
 %\\
@@
 %     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
-%    	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
-%    	\Pred_{\symb{sv}}(SV_k,\alpha_m^{m\in (I_1\uplus I_2)},\beta_j^{j\in J},\alpha)\\ 
-%    		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
-%    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
+%    	\Pred = \bigwedge_{m\in I_1\uplus I_2}\!\! \Pred_m \land
+%    	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2},\beta_j^{j\in J},\alpha)\\ 
+%    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
 %    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
 %    }
-%    {\mylangle \overline{\pNet}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
+%    {\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
 %    	\models
@@
 %    		{
-%    		{\beta_j}^{j\in J^\prime}, \Pred, \uplus_{m\in I_1\uplus I_2} 
+%    		{\beta_j}^{j\in J^\prime}, \Pred,  \biguplus_{m\in I_1\uplus I_2} 
 %    		\Post_m}
@@
 %\end{mathpar}
-	\noindent
-\begin{mathpar}
-    \mprset {vskip=.8ex}
-\inferrule
-    {
-\Leaves(\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in 
-    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
-k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
-\\
-\\     	
-	\forall m\!\!\in\!\! I_1. {\pNet_m 
-	\models\openrule
-    	{
-    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
-    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
-    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
-  \qquad
-\forall m\!\!\in\!\! I_2.		{ \pNet_m 
-    	 \models
-    	\openrule
-    	{\emptyset, \Pred_m, \Post_m}
-    	{\ostate{s_m} \OTarrow {\alpha_m}
-    		\ostate{s_m'}} }\\\\
-     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
-    	\Pred = \bigwedge_{m\in I_1\uplus I_2}\!\! \Pred_m \land
-    	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2},\beta_j^{j\in J},\alpha)\\ 
-    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
-    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
-    }
-    {\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
-    	\models
-    	{\openrule
-    		{
-    		{\beta_j}^{j\in J^\prime}, \Pred,  \biguplus_{m\in I_1\uplus I_2} 
-    		\Post_m}
-    		{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
-    			\ostate{(s_i^\prime)^{i\in L}}}
-    	}
-    }
-\end{mathpar}
-
-\todoLHin{add a paragraph about pnets properties and usage, here are a few points (to be completed and written up properly depending on what we need}
-
-- pnets as a model for gcm components (behaviour, distributed systems, verification)
-
-- used for finite model checking (with finite domains for parameters)
-
-- smt framework for reasoning on infinite models
-
-- a theory of pnets: composition properties , stong (and weak) bisim
-	** extract a few useful composition theorems? **
+
+pNets have already been used to define a behavioural semantics for distributed components~\cite{AmeurBoulifa2017}, in these works, from a pNet model with finite instantiations of parameters, correctness properties can be verified by model-checking.
+More recently, a bisimulation theory with composition properties have been formalised for open pNets~\cite{HMZ-FORTE2016}, and a SMT framework has been developed  for verifying properties of parametrised open pNets.
+
+%\todoLHin{add a paragraph about pnets properties and usage, here are a few points (to be completed and written up properly depending on what we need}
+%
+%- pnets as a model for gcm components (behaviour, distributed systems, verification)
+%
+%- used for finite model checking (with finite domains for parameters)
+%
+%- smt framework for reasoning on infinite models
+%
+%- a theory of pnets: composition properties , stong (and weak) bisim
+%	** extract a few useful composition theorems? **
 
@@
 %    $
-	\medskip
 %        \TODO{may be explain how $\Pred(SV,a_i^{i\in I_k},b_j^{j\in
@@
 	%%include it, because it may change the decidability conditions on predicates}
-
-\end{definition}
 

### 2019-01-23 2016-Weak-FH-Bisim/WeakBisim.tex

@@
 
-By using  Lemma \ref{lem-rel-OT-WOT} we can conclude from case 1 and 2 that we have:
+By using  Lemma \ref{lem-rel-OT-WOT} we can conclude from case 1, 2 and 3 that we have:
 \begin{mathpar}
@@
 
-\TODO{We will add side conditions ?? }\\
+$s_l=s_{0l} \wedge s_{{m_1}l}=t_l \wedge t'_l = u_{0l} \wedge s'_l=s_{{m_2}l}$
+\TODO{Avant d'ajouter la suite, il faudrait se mettre d'accord sur les notations}\\
 
@@
 We proceed in the same way as for states named $u$.
-
-Therefore, we will obtain:
-
+We also consider for the third case $Q$  moves, i.e, $\ostate{t_l^{l\in L_Q}} \neq \ostate{t_l'^{\,l\in L_Q}}$.
+So we have: \\
 $\forall p \in [0\ldots n_1] Q\models{\openrule
@@
 $\\
+
 such that $n_1 \leq m_1$ and $n_2 \leq m_2$\\
-\TODO{We will discuss}
-
-For each  $\symb{OT}_p$ of $Q$ such that $p \in S$ and $S \subseteq [0\ldots (m_1\!+\!m_2)\!+\!1]$ in the form:
+
+Let us consider the first item, in the series of $(n_1+1)$  actions $\alpha_p$ some of them may be non-observable ($\tau$ transition).
+By considering $\tau$  actions we split the sequence of $n_1+1$ actions into subsequences, such that each subsequence is a series of  $\tau$ transitions  ending by not more than one observable transition.
+For each subsequence we can write the  following:\\
+$Q\models{\openrule
+			{
+				(\beta_{i})_j^{j\in J\cap\Holes(Q)}, {{\Pred_i}\!\!''},  
+				{{\Post_i}\!\!''}}
+				{\ostate{s_{il}^{l\in L_Q}} \OTarrow {\tau}
+				\ostate{s_{(i+1)l}^{l\in L_Q}}}
+				}%\]
+, Q\models{\openrule
+			{
+				(\beta_{(i+1)})_j^{j\in J\cap\Holes(Q)}, {{\Pred''_{(i+1)}}},  
+				{{\Post''_{(i+1)}}}}
+				{\ostate{s_{(i+1)l}^{l\in L_Q}} \OTarrow {\tau}
+				\ostate{s_{(i+2)l}^{l\in L_Q}}}
+				}%\]
+\ldots\\
+Q\models{\openrule
+			{
+				(\beta_{k})_j^{j\in J\cap\Holes(Q)}, {{\Pred_k}\!\!''},  
+				{{\Post_j}\!\!''}}
+				{\ostate{s_{kl}^{l\in L_Q}} \OTarrow {\alpha_k}
+				\ostate{s_{(k+1)l}^{l\in L_Q}}}
+				}%\]
+$\hspace{0.5cm}
+where $1\leq i<n_1$ and $i<k$.\\
+By Lemma \ref{lem-rel-OT-WOT} we obtain the following weak open transition:
+\begin{mathpar}
+Q\models{\openrule
+			{
+			(\gamma_p)_j^{j\in J\cap\Holes(Q)}, {\Pred_p}, {\Post_p}}
+			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha_{k}}
+				\ostate{s_{(p+1)l}^{l\in L_Q}}}
+		}%\]
+\end{mathpar}
+
+where $s_{il} = s_{pl}$ and $s_{(p+1)l}=s_{(k+1)l}$ 
+\TODO{et le reste}
+
+Particular attention should be paid to the last subsequence which may not end by an observable action.
+We proceed in the same way we obtain an non-observable weak open transition; and by applying  rule (\WTTrois) to the resulting non-observable weak open transition and the previous weak open transition we obtain a weak open transition.
+
+By iterating this reasoning over the states $u$ and $t$  one have that: for each  $\symb{OT}_p$ of $Q$ such that $p \in S$ and $S \subseteq [0\ldots (n_1\!+\!n_2)\!+\!1]$ in the form and $\alpha_p \neq \tau$:
 \begin{mathpar}
@@
 \end{mathpar}
-By rule (\WTTrois)  we can conclude that  we have:
+We can conclude that we have a $\symb{WOT}_p$:
 \begin{mathpar}
@@
 such that $\gamma_p = \vis{\beta_p}$.
-\TODO{maybe it is better to use $\gamma_p=[\beta_p]$}\\
+\TODO{le reste une fois mis d'accord sur la notation}\\
+
+In this case, the number of weak open transitions
+might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.
+
+\TODO{I STOPPED THERE!!!}
 

### 2019-01-23 2018-Arch-pNets/arch-pNets.tex
Merged previous works into one seciton
a few items in the related works

@@
 
-\section{Preliminaries}
+\section{Previous results: Architecture and pNets}
+
+\subsection{Preliminaries}
 \label{secn:preliminaries}
@@
 
-\subsection{Notations}
+\subsubsection{Notations}
 \label{secn:notations}
@@
 
-\subsection{Term algebra}
+\subsubsection{Term algebra}
 \label{secn:terms}
@@
 
-\section{The theory of architectures with data}
+\subsection{The theory of architectures with data}
 \label{secn:archs}
@@
 
-\subsection{Components and composition}
+\subsubsection{Components and composition}
 \label{secn:components}
@@
 %****************************************************************
-\subsection{Architectures}
+\subsubsection{Architectures}
 \label{secn:archi}
@@
 %****************************************************************
-\subsection{Preservation of safety properties}
+\subsubsection{Preservation of safety properties}
 \label{secn:safety}
@@
 
-\section{Open pNets}
+\subsection{Open pNets}
 \label{secn:pNets}
@@
 %notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
-\begin{definition}[Open transitions]
+\begin{definition}[Open transition]
 	\label{defn:OpenTransitions}
@@
 
-\section{SMT encoding of open pNets}
+\subsection{SMT encoding of open pNets}
 \label{secn:smt}
@@
 \label{secn:related}
+Previous works on pNets and BIP architectures have been mentioned at the beginning of the paper.
+Consequently, we  review here the closest related works outside the scope of pNets and BIP architectures.
+Among those, we focus on existing approaches for the compositional and parameterized verification of systems, and on alternative verification engines???
+\noteLH{not sure about this classification ; to be refined}
+
+A few tracks
+
+%%% compositional verification
+approaches by typing interfaces/protocols
+
+infinite/parametrized model checking?
+
+theorem proving? (too much manual effort) we need an example, we could cite Coqcots and Pycots for reconfiguration
+
+SMT on an application not using component structure. is there a strong Z3 example
+
+KeY? (I would call this symbolic execution and assume-guarantee)
 
 %****************************************************************
+
 %****************************************************************

### 2019-01-23 2018-Arch-pNets/arch-pNets.tex
arch-pNets: (Minor) clean-up, including one of the properties in Example 1.

@@
   %
-  \todoSB{Do we actually need this?}\todoLH{I agree: I do not think we need this}
-  \hl{The \emph{closed semantics} of $B$ is given by the LTS denoted
-  $\semclosed{B} \bydef{=}\reachable{\semopen{B}}$, comprising
-  only the reachable states of $\semopen{B}$.}
+  %% \todoSB{Do we actually need this?}\todoLH{I agree: I do not think we need this}
+  %% \hl{The \emph{closed semantics} of $B$ is given by the LTS denoted
+  %% $\semclosed{B} \bydef{=}\reachable{\semopen{B}}$, comprising
+  %% only the reachable states of $\semopen{B}$.}
 \end{definition}
@@
     \end{equation}
-  \item A timeout can only occur within the specified delay after
+  \item A reset can only be requested within the specified delay after
     a failure:
@@
       \\
-      \AW[]{\bigl((\PortTOC \land \NameTimer.t = T_1) \rightarrow
+      \AW[]{\bigl((\PortAsk \land \NameTimer.t = T_1) \rightarrow
         (T_1 - T_0 \in \NameCtrl.\mathit{zone})\bigr)

### 2019-01-24 2016-Weak-FH-Bisim/WeakBisim.tex
small sentence over skype

@@
 We proceed in the same way as for states named $u$.
-We also consider for the third case $Q$  moves, i.e, $\ostate{t_l^{l\in L_Q}} \neq \ostate{t_l'^{\,l\in L_Q}}$.
+To simplify the proof, we consider that in 3, $Q$  moves, i.e, $\ostate{t_l^{l\in L_Q}} \neq \ostate{t_l'^{\,l\in L_Q}}$, else transition 3 of $Q$ should be skipped and the last $s_{p l}$ are equal to the first $u_{0 l$.
 So we have: \\

### 2019-01-25 2018-Arch-pNets/arch-pNets.tex

@@
 \soulregister{\eg}{0}
+\soulregister{\Eg}{0}
 \soulregister{\wrt}{0}
@@
   \setTupleDelims[(]{)}%
+  \tuplebase[#1]{#2}%
+}
+
+\newcommand{\btuple}[2][\ensuremath{,\allowbreak}]{%
+  \setTupleDelims[\bigl(]{\bigr)}%
   \tuplebase[#1]{#2}%
@@
 \newcommand{\eg}[1][\ ]{e.g.#1}
+\newcommand{\Eg}[1][\ ]{E.g.#1}
 \newcommand{\cf}[1][\ ]{cf.#1}
@@
 intervals ordered by inclusion.
+%
+\addSB{In practice, and in the examples of
+this paper, all the variables are sorted, meaning that their values
+can only range over given subsets of $\data$, such as $\sB$ or
+$\sB^<$.
+%
+When speaking of an ordered sort, \eg $\sB^<$, we will assume that it
+forms a meet-semilattice and denote by $\wedge$ the corresponding meet
+operator.}
 
@@
 %
-\addSB{
-%
-It is important to observe that in practice, and in the examples of
-this paper, all the variables are sorted, meaning that their values
-can only range over given subsets of $\data$, such as $\sB$ or
-$\sB^<$.  Hence, applied to expressions, valuations should be
-interpreted as partial functions $\exprs{V} \rightharpoonup
-\data$\footnote{
-%
-
-%
-}
-%
-}
+\addSB{Since we consider variables to be sorted, valuations
+  applied to expressions are interpreted as partial functions
+  $\exprs{V} \rightharpoonup \data$.}
 
@@
 For two valuations $\val{1}{}, \val{2}{} : V \rightarrow
-\data$, we denote \[\valdiff{\val{1}{}}{\val{2}{}} \bydef{=}
-\bsetdef{v \in V}{\val{1}{}(v) \neq \val{2}{}(v)}\] the set of
+\data$, we denote $\valdiff{\val{1}{}}{\val{2}{}} \bydef{=}
+\bsetdef{x \in V}{\val{1}{}(x) \neq \val{2}{}(x)}$ the set of
 variables that are assigned different values by the two
@@
 
-\noteSBin{%
-To guarantee preservation of properties guards and expressions
-have to be \emph{monotonic}.  In the case of a trivial order, \ie
-when nothing is comparable, \emph{any guard or expression is
-  monotonic}.  Thus, this is not really a constraint!
-
-Do we put this in the definition of expressions and guards or in
-the definitions of components and interaction models?
-}
+%% \noteSBin{%
+%% To guarantee preservation of properties guards and expressions
+%% have to be \emph{monotonic}.  In the case of a trivial order, \ie
+%% when nothing is comparable, \emph{any guard or expression is
+%%   monotonic}.  Thus, this is not really a constraint!
+
+%% Do we put this in the definition of expressions and guards or in
+%% the definitions of components and interaction models?
+%% }
 
@@
   \item $\goesto{}\, \subseteq
-    Q \times 2^P \times \guards{V} \times \updates{V} \times Q$
+    Q \times (2^P\setminus \{\emptyset\}) \times \guards{V} \times \updates{V} \times Q$
 %
     is a \emph{transition relation}, with transitions
-    labelled by \emph{interactions}, \ie triples consisting of a non-empty set of ports
-    $\emptyset \neq a \subseteq P$, a monotonic Boolean \emph{guard} $g \in
-    \guards{V}$ and a monotonic \emph{update assignment} \hl{$u \in
-    \updates{V}$}.
+    labelled by \emph{interactions}, \ie triples consisting of a non-empty set of ports,
+    %% $\emptyset \neq a \subseteq P$,
+    a monotonic Boolean \emph{guard}
+    %% $g \in \guards{V}$ 
+    and a monotonic \emph{update assignment}.
+    %% \hl{$u \in \updates{V}$}.
   \end{itemize}
@@
   \centering
-  \includegraphics[width=\columnwidth]{BIPspec-ArchFailureTimerMax-v4}
+  \includegraphics[width=0.9\columnwidth]{BIPspec-ArchFailureTimerMax-v4}
   \caption{The BIP specification of the Failure Monitor architecture}
@@
 
-The model in \fig{schema:ArchFailure:BIP} has two components:
+The model in \fig{schema:ArchFailure:BIP} has  components
 %% The
@@
 %
-$\NameTimer$ and $\NameCtrl$, with interfaces
-\[\bigl(
+$\NameTimer$(imer) and $\NameCtrl$(ontrol), with interfaces
+$\btuple{
   \{t, z\},
   \{\PortTick, \PortCancel, \PortTOT\},
-\export[\NameTimer]
-\bigr)\,,
-\qquad
-\export[\NameTimer](p) =
-\begin{cases}
-  \{t, z\}, & \text{if } p = \PortTick,\\
-  \emptyset, & \text{otherwise}
-\end{cases}
-\]
+  \bigl\{\PortTick \mapsto \{t, z\}\bigr\}
+}$,
 and
-\[\bigl(
+$\btuple{
   \{\mathit{zone}\},
   \{\PortReset, \PortFail, \PortResume, \PortTOC\},
-\export[\NameCtrl]
-\bigr)\,,
-\quad
-\export[\NameCtrl](p) =
-\begin{cases}
-  \{\mathit{zone}\}, & \text{if } p = \PortFail,\\
-  \emptyset, & \text{otherwise}
-\end{cases}
-\]
-%
-respectively. %% , where $\export[\NameCtrl](\PortFail) =
+  \bigl\{\PortFail \mapsto \{\mathit{zone}\}\bigr\}
+}$, respectively.
+%
+%% \[
+%% \begin{array}{@{}c@{\hspace{3mm}}c@{}}
+%%   \bigl(
+%%   \{t, z\},
+%%   \{\PortTick, \PortCancel, \PortTOT\},
+%%   \export[\NameTimer]
+%%   \bigr)\,,
+%%   %% \qquad
+%%   &
+%%   \bigl(
+%%   \{\mathit{zone}\},
+%%   \{\PortReset, \PortFail, \PortResume, \PortTOC\},
+%%   \export[\NameCtrl]
+%%   \bigr)\,,
+%%   \\
+%%   \export[\NameTimer](p) =
+%%   \begin{cases}
+%%     \{t, z\}, & \text{if } p = \PortTick,\\
+%%     \emptyset, & \text{otherwise,}
+%%   \end{cases}
+%%   %% \]
+%%   %% and
+%%   %% \[
+%%   %% \quad
+%%   &
+%%   \export[\NameCtrl](p) =
+%%   \begin{cases}
+%%     \{\mathit{zone}\}, & \text{if } p = \PortFail,\\
+%%     \emptyset, & \text{otherwise.}
+%%   \end{cases}
+%% \end{array}
+%% \]
+%
+%% , where $\export[\NameCtrl](\PortFail) =
 %% \{\mathit{zone}\}$ and $\export[\NameCtrl](p) = \emptyset$, for all
@@
 %% \emph{behaviour}.
-Component \emph{behaviour} is defined by states ($\{\cstate{0},
-\cstate{1}, \cstate{2}\}$, for $\NameCtrl$; $\{\tstate{0}\}$, for
-$\NameTimer$) and transitions.
-%
-Transitions are labelled with the ports of the
+Component \emph{behaviour} is defined by states %% ($\{\cstate{0},
+%% \cstate{1}, \cstate{2}\}$, for $\NameCtrl$; $\{\tstate{0}\}$, for
+%% $\NameTimer$)
+and transitions.
+The initial states
+\tstate{0} and \cstate{0}, and valuations $\val{0}{\NameTimer} = \{t
+\mapsto 0, z \mapsto \topinterval\}$ and $\val{0}{\NameCtrl} =
+\{\mathit{zone} \mapsto [\mathrm{Min}, \mathrm{Max}]\}$ are shown by
+the incoming arrows $\goesto{\TimerInit[]} \tstate{0}$ and
+$\goesto{\IntervalInit[]} \cstate{0}$.\footnote{%
+%
+  We use $\topinterval$ to denote the top interval in the inclusion
+  order, \ie $(-\infty, +\infty)$.
+%
+} The constants $\mathrm{Min}$ and $\mathrm{Max}$ are the parameters
+of the architecture.
+
+Transitions are labelled with ports of the
 corresponding components, Boolean guards and update assignments on local
-variables.  For instance, the loop transition $\tstate{0}
+variables.  \Eg[,] the loop transition $\tstate{0}
 \goesto{\PortTick, \GuardTick[], \TimerUpd[]} \tstate{0}$ in the
-$\NameTimer$ component is labeled by the port $\PortTick$, it can be
+component $\NameTimer$ is labeled by the port $\PortTick$.  It can be
 fired only when the current value of the local variable $t$ is less
@@
 omitted.  The default values are the constant predicate $\true$ (true) and
-the empty assignment {\noop}, respectively.  The initial states
-\tstate{0} and \cstate{0}, and valuations $\val{0}{\NameTimer} = \{t
-\mapsto 0, z \mapsto \topinterval\}$ and $\val{0}{\NameCtrl} =
-\{\mathit{zone} \mapsto [\mathrm{Min}, \mathrm{Max}]\}$ are shown by
-incoming arrows $\goesto{\TimerInit[]} \tstate{0}$ and
-$\goesto{\IntervalInit[]} \cstate{0}$, respectively.\footnote{%
-%
-  We use $\topinterval$ to denote the top interval in the inclusion
-  order, \ie $(-\infty, +\infty)$.
-%
-} The constants $\mathrm{Min}$ and $\mathrm{Max}$ are the parameters
-of the architecture.
+the empty assignment {\noop}, respectively.  
 %\noteLH{It looks like Max is in zone, I do not understand}
-
-\todoSBin{Speak of guard monotonicity}
+%
+Clearly, all guards and update assignments are monotonic.
+
+%% \todoSBin{Speak of guard monotonicity}
 
@@
   \label{defn:comp:semantics}
-  The \emph{open semantics} of a component $B = \tuple{Q, q^0, V,
-  \val{0}{}, P, \export, \goesto{}}$ is given by the LTS denoted $\semopen{B} = \tuple{S,
+  The \emph{semantics} of a component $B = \tuple{Q, q^0, V,
+  \val{0}{}, P, \export, \goesto{}}$ is %% given by
+  the LTS denoted $\semopen{B} = \tuple{S,
   s^0, \goesto{}}$, where $S = Q \times \valuations{V}$, $s^0 =
@@
   \label{defn:im}
-  Consider a finite set of component interfaces $(V_i, P_i,
+  For a finite set of component interfaces $(V_i, P_i,
   \export[i])^{i \in I}$, such that all $P_i$ and all $V_i$ are
-  pairwise disjoint, \ie $\forall i \neq j,\ P_i \cap P_j = V_i \cap
-  V_j = \emptyset$.  Let $P = \bigcup_{i \in I} P_i$, $V = \bigcup_{i
+  pairwise disjoint, %% \ie $\forall i \neq j,\ P_i \cap P_j = V_i \cap
+  %% V_j = \emptyset$. 
+  let $P = \bigcup_{i \in I} P_i$, $V = \bigcup_{i
     \in I} V_i$ and $\export : P \rightarrow 2^V$ such that, for any
@@
 %
-  \begin{gather}
+  \begin{gather*}
 %%     \label{eq:im:empty}
@@
     }\,.
-  \end{gather}
-  \todoSBin{Add the intuitive explanation}
+  \end{gather*}
+  %% \todoSBin{Add the intuitive explanation}
 \end{definition}
+
+\addSB{Intuitively, an interaction can be fired if all the involved
+  components are ready to fire their corresponding transitions.  The
+  other components do not change their states.  Both the interaction
+  guard and those of the participating transitions must be satisfied.
+  The update assignment of the interaction is executed first, followed
+  by those of the components.}
 
@@
 at the leaves.  They define sets of interactions, based on the
-attributes of the connected ports, which may be either \emph{trigger}
+attributes of the nodes, which may be either \emph{trigger}
 (triangles in \fig{schema:ArchFailure:BIP}) or \emph{synchron}
@@
 If all sub-connectors of a connector are synchrons, then an
-interaction may be executed by the connector only if each subconnector
+interaction is allowed by the connector only if each subconnector
 can contribute.
@@
 If at least one of the sub-connectors is a trigger, then any
-interaction consisting of contributions of any set of sub-connectors,
-\emph{involving at least one of the triggers}, can be executed.
-The composition semantics of BIP systems consists in
-firing exactly one interaction, enabled through at least one of the
-top-level connectors, at each execution round.
-
-\todoSB{Update this}
-\hl{For instance, in \fig{schema:ArchFailure:BIP}, the two ports
-$\NameTimer.\PortStart$ and $\NameCtrl.\PortFail$ are always
-synchronised, since they belong to exactly one binary sub-connector,
-where they are both synchrons.  In particular, this means that
-whenever the transition \cstate{0} \goesto{\PortFail} \cstate{1} is
-fired, so is the transition \tstate{0} \goesto{\PortStart,
-  \TimerInit[]} \tstate{1}, initialising the timer.  The binary
-connector $\NameTimer.\PortStart \twosynch
-\NameCtrl.\PortFail$ is a sub-connector of a hierarchical connector,
-where the port $\NameOprnd.\PortFail$ is a trigger.  Thus, the above
-interaction can only happen together with $\NameOprnd.\PortFail$,
-forming a ternary interaction.  On the contrary, being a trigger, the
-port $\NameOprnd.\PortFail$ can fire alone, forming a singleton
-interaction.}
-
-\todoSBin{Speak of data transfer}
-
-\todoSBin{Provide the interaction model}
+interaction consisting of contributions of any set of sub-connectors
+\emph{involving at least one of the triggers} is allowed.
+%
+The interaction model is defined as the set of all interactions
+allowed by at least one of the connectors in the system.
+%% The composition semantics of BIP systems consists in
+%% firing exactly one interaction, enabled through at least one of the
+%% top-level connectors, at each execution round.
+
+For instance, the connector {\NameTimer.\PortTick
+  \trigsynch (\PortFail \trigsynch \NameCtrl.\PortFail)} is a
+two-level hierarchical connector.  In the second-level subconnector
+{\PortFail \trigsynch \NameCtrl.\PortFail}, the port {\PortFail} is a
+trigger, whereas {\NameCtrl.\PortFail} is a synchron.  Therefore, this
+subconnector allows two interactions labelled $\{\PortFail\}$ and $\listset{\NameCtrl.\PortFail, \PortFail}$.  Similarly, at the top level,
+{\NameTimer.\PortTick} is a trigger, whereas the second-level
+subconnector is a synchron.  Hence, the overall connector allows the
+interaction involving only one port {\NameTimer.\PortTick}\footnote{%
+%
+  Such interactions are called \emph{singleton interactions}.
+%
+} and any interaction involving both {\NameTimer.\PortTick} and
+\emph{some} interaction of the second-level subconnector.  Combining
+the two levels we can see that the entire connector defines the
+following three interactions (observe that $\topinterval +
+\NameTimer.t = \topinterval$ and $\NameTimer.z \cap \topinterval =
+\NameTimer.z$):
+%
+\begin{gather*}
+  \bigl(\{\NameTimer.\PortTick\},
+  \true, \emptyset\bigr)
+  %% \NameTimer.z := \NameTimer.z\bigr)
+  ,
+%
+  \qquad
+%
+  \bigl(\{\PortFail, \NameTimer.\PortTick\},
+  \true, \emptyset\bigr)
+  %% \NameTimer.z := \NameTimer.z\bigr)
+  ,
+%
+  \\
+%
+  \bigl(\{\NameCtrl.\PortFail, \PortFail, \NameTimer.\PortTick \},
+  \true,
+  \NameTimer.z := \NameTimer.z \cap (\NameCtrl.\mathit{zone} + \NameTimer.t)\bigr)
+  .
+\end{gather*}
+%% \begin{align*}
+%%   \bigl(\{\NameTimer.\PortTick\}&,
+%%   \true, 
+%%   \NameTimer.z := \NameTimer.z\bigr)
+%%   \,,\\
+%%   \bigl(\{\PortFail, \NameTimer.\PortTick\}&,
+%%   \true,
+%%   \NameTimer.z := \NameTimer.z\bigr)
+%%   \,,\\
+%%   \bigl(\{\NameCtrl.\PortFail, \PortFail, \NameTimer.\PortTick \}&,
+%%   \true,
+%%   \NameTimer.z := \NameTimer.z \cap (\NameCtrl.\mathit{zone} + \NameTimer.t)\bigr)
+%%   \,.
+%% \end{align*}
+
+%% \todoSB{Update this}
+%% \hl{For instance, in \fig{schema:ArchFailure:BIP}, the two ports
+%% $\NameTimer.\PortStart$ and $\NameCtrl.\PortFail$ are always
+%% synchronised, since they belong to exactly one binary sub-connector,
+%% where they are both synchrons.  In particular, this means that
+%% whenever the transition \cstate{0} \goesto{\PortFail} \cstate{1} is
+%% fired, so is the transition \tstate{0} \goesto{\PortStart,
+%%   \TimerInit[]} \tstate{1}, initialising the timer.  The binary
+%% connector $\NameTimer.\PortStart \twosynch
+%% \NameCtrl.\PortFail$ is a sub-connector of a hierarchical connector,
+%% where the port $\NameOprnd.\PortFail$ is a trigger.  Thus, the above
+%% interaction can only happen together with $\NameOprnd.\PortFail$,
+%% forming a ternary interaction.  On the contrary, being a trigger, the
+%% port $\NameOprnd.\PortFail$ can fire alone, forming a singleton
+%% interaction.}
+
+%% \todoSBin{Speak of data transfer}
+
+%% \todoSBin{Provide the interaction model}
 
@@
 
-  We write $\alpha \prec_\pi \beta$ for $(\alpha, \beta) \in \pi$ and 
-  denote $\filter{\alpha} \bydef{=} \bsetdef{\beta \in (2^P \times
-    \guards{V} \times \updates{V})}{\alpha \prec_\pi \beta}$ the set of
+  We write $\alpha \prec_\pi \beta$, for $(\alpha, \beta) \in \pi$, and 
+   $\filter{\alpha} \bydef{=} \bsetdef{\beta \in (2^P \times
+    \guards{V} \times \updates{V})}{\alpha \prec_\pi \beta}$, for the set of
   interactions that have higher priority than $\alpha$.
@@
   \goesto[\pi]{}}$, where $\goesto[\pi]{}$ is the minimal transition
-  relation satisfying the rule
-%
-  \begin{equation}
+  relation satisfying the rule (we denote
+  $\filter[q]{\alpha} \bydef{=} %% \filter{\alpha} \cap
+  %% \bsetdef{\beta \in (2^P \times \guards{V} \times \updates{V})}
+  \setdef{\beta \in \filter{\alpha}}{q \goesto{\beta}}$)
+%
+  \begin{equation*}
     \label{eq:priority:sem}
@@
       q \goesto[\pi]{a, g', u} q'
-    }\,, 
-  \end{equation}
-%
-  where $\filter[q]{\alpha} \bydef{=} %% \filter{\alpha} \cap
-  %% \bsetdef{\beta \in (2^P \times \guards{V} \times \updates{V})}
-  \setdef{\beta \in \filter{\alpha}}{q \goesto{\beta}}$.
-  \todoSBin{Add the intuitive explanation}
+    }\,.
+  \end{equation*}
+%
+  %% \todoSBin{Add the intuitive explanation}
 \end{definition}
+
+\addSB{Intuitively, an interaction can be fired only if all the
+higher-priority interactions available in the current state are
+disabled by their respective guards.}
 
@@
 obtained results to other priority models.
+%
+Below, we will assume that the maximal progress priority $\mu$ is
+applied after each composition with an interaction model.
 
@@
 %% $a \subset b$ (as sets of ports), $b$ has higher priority than $a$.
-Going back to our running example in \fig{schema:ArchFailure:BIP}, under the maximal progress priority, the
-port $\NameOprnd.\PortFail$ will never fire alone in a global state,
-where both $\NameTimer.\PortStart$ and $\NameCtrl.\PortFail$ are
-enabled.
+In our running example, under the maximal progress priority, the
+port $\NameTimer.\PortTick$ will never fire alone in a global state,
+where the \noteSB{This turns out to be the first use of the word. I am tempted to pretend I did not notice.}\hl{dangling} port $\PortFail$ is also enabled.
 
@@
 
-\begin{note}
-  \label{rem:maxprogress}
-  Below, we will assume that the maximal progress priority $\mu$ is
-  applied after each composition with an interaction model.
-\end{note}
+%% \begin{note}
+%%   \label{rem:maxprogress}
+%% \end{note}
 
@@
 
-\todoSBin{Sort out the following two paragraphs}
-
-Contrary to standard BIP models, architectures comprise one or several
-\emph{operand} components, whereof only the set of \emph{ports} is
-given.  Here, the operand component is $\NameOprnd$ and its interface
-consists of the ports $\PortFinish$, $\PortResume$ and $\PortFail$.
-
-Application of the Failure Monitor architecture ensures that, whenever
-a failure is registered in the operand component, the system will be
-reset, unless a resumption is registered within $\mathrm{Max}$ time
-units (more details in Sect.~\ref{section:resultOA}).
-
-\noteLHin{should we say that always epsilon C is the epsilon of C?}
+Architectures are partially defined BIP models, where \emph{dangling}
+ports serve as placeholders for the eventual connection with
+additional \emph{operand} components.
+
+%% Contrary to standard BIP models, architectures comprise one or several
+%% \emph{operand} components, whereof only the set of \emph{ports} is
+%% given.  Here, the operand component is $\NameOprnd$ and its interface
+%% consists of the ports $\PortFinish$, $\PortResume$ and $\PortFail$.
+
+%% Application of the Failure Monitor architecture ensures that, whenever
+%% a failure is registered in the operand component, the system will be
+%% reset, unless a resumption is registered within $\mathrm{Max}$ time
+%% units (more details in Sect.~\ref{section:resultOA}).
+
+%% \noteLHin{should we say that always epsilon C is the epsilon of C?}
 
@@
 \item
-  $\cC$ is a finite set of \emph{coordinating components}
-  with pairwise disjoint sets of ports and variables, such that
+  $\cC$ is a finite set of \emph{coordinating components},
+  %% with pairwise disjoint sets of ports and variables,
+  such that
   $\bigcup_{C \in \cC} P_C \subseteq P_A$ and
@@
 \item
-  $\Gamma \subseteq 2^{P_A} \times \guards{V_A} \times \exprs{V_A}$
+  $\Gamma \subseteq 2^{P_A} \times \guards{V_A} \times \updates{V_A}$
   is an interaction model over $(V_A, P_A, \export[A])$.
@@
   be a set of components, such that
-%
-  \begin{align}
-    \bigcup_{B \in \cB} V_B \cap \bigcup_{C \in \cC} V_C = \emptyset\,,
-    &&
-    V_A \subseteq V \bydef{=} \bigcup_{B \in \cB \cup \cC} V_B\,,
-    \\
-    \bigcup_{B \in \cB} P_B \cap \bigcup_{C \in \cC} P_C = \emptyset\,,
-    &&
-    P_A \subseteq P \bydef{=} \bigcup_{B \in \cB \cup \cC} P_B\,,
-  \end{align}
-%
-  \hl{and $\export[A](p) = V_A \cap \export[B](p)$, for any $B \in \cB$
-  and $p \in P_A \cap P_B$.}
+  $V_A \subseteq V \bydef{=} \bigcup_{B \in \cB \cup \cC} V_B$,
+  $P_A \subseteq P \bydef{=} \bigcup_{B \in \cB \cup \cC} P_B$
+%
+  %% \begin{align}
+  %%   \bigcup_{B \in \cB} V_B \cap \bigcup_{C \in \cC} V_C = \emptyset\,,
+  %%   &&
+  %%   V_A \subseteq V \bydef{=} \bigcup_{B \in \cB \cup \cC} V_B\,,
+  %%   \\
+  %%   \bigcup_{B \in \cB} P_B \cap \bigcup_{C \in \cC} P_C = \emptyset\,,
+  %%   &&
+  %%   P_A \subseteq P \bydef{=} \bigcup_{B \in \cB \cup \cC} P_B\,,
+  %% \end{align}
+%
+  and $\export[A](p) = V_A \cap \export[B](p)$, for any $B \in \cB$
+  and $p \in P_A \cap P_B$.
 %
@@
 %
-  $\IMextend{\Gamma}{P}$ is the \emph{extension} of the interaction
-  model $\Gamma$ to the set of ports $P$, \ie the interaction model
+  $\IMextend{\Gamma}{P} \bydef{=}
+  \bsetdef{
+    (a, g, u)
+  }{
+    a \subseteq P,
+    (a \cap P_A, g, u) \in \Gamma
+  }$
+  is
+  %% is the \emph{extension} of the interaction
+  %% model $\Gamma$ to the set of ports $P$, \ie
+  the interaction model
   over $(V, P, \export)$, with
@@
   \]
-  defined by\noteLH{looks like this also depends on Pa}
-%
-  \noteSB{It does, indeed.  To be completely rigorous, I could replace
-    this with something like $\Gamma\uparrow_{P_A}^P$ but this is
-    quite heavy and the dependency is already implicit from the fact
-    that $\Gamma$ is defined on $P_A$}
-%
-  \noteSB{Which one of \eq{im:extension} and \eq{im:extension1} is
-    more intuitive?}
-%
-  \begin{align}
-    \label{eq:im:extension}
-    \IMextend{\Gamma}{P} &\bydef{=}
-    \bsetdef{
-      (a \cup a', g, e)
-    }{
-      (a, g, e) \in \Gamma, a' \subseteq P \setminus P_A
-    }
-    \\
-    \label{eq:im:extension1}
-    &= 
-    \bsetdef{
-      (a, g, e)
-    }{
-      a \subseteq P,
-      (a \cap P_A, g, e) \in \Gamma
-    }
-  \end{align}
+%% defined by \noteLH{looks like this also depends on Pa}
+%% %
+%%   \noteSB{It does, indeed.  To be completely rigorous, I could replace
+%%     this with something like $\Gamma\uparrow_{P_A}^P$ but this is
+%%     quite heavy and the dependency is already implicit from the fact
+%%     that $\Gamma$ is defined on $P_A$}
+%% %
+%%   \noteSB{Which one of \eq{im:extension} and \eq{im:extension1} is
+%%     more intuitive?}
+%
+  %% \begin{align}
+  %%   \label{eq:im:extension}
+  %%   \IMextend{\Gamma}{P} &\bydef{=}
+  %%   \bsetdef{
+  %%     (a \cup a', g, e)
+  %%   }{
+  %%     (a, g, e) \in \Gamma, a' \subseteq P \setminus P_A
+  %%   }
+  %%   \\
+  %%   \label{eq:im:extension1}
+  %%   &= 
+  %%   \bsetdef{
+  %%     (a, g, e)
+  %%   }{
+  %%     a \subseteq P,
+  %%     (a \cap P_A, g, e) \in \Gamma
+  %%   }
+  %% \end{align}
 %
@@
 
-\todoSBin{Define equivalence $\arequiv$?}
+%% \todoSBin{Define equivalence $\arequiv$?}
 
 An architecture $A$ enforces coordination constraints on the
-components in $\cB$.  The interface \hl{$(V_A, P_A, \export[A])$} of an
+components in $\cB$.  The interface $(V_A, P_A, \export[A])$ of an
 architecture $A$ contains all ports of the coordinating
-components $\cC$ and some additional ports, which must belong to
+components $\cC$ and the dangling ports, which must belong to
 the components in $\cB$.  In the application $A(\cB)$, the ports
@@
 not belong to $P_A$ are not restricted and can participate in any
-interaction.  In particular, they can join the interactions in
-$\Gamma$ (see \eq{im:extension}).  If the interface of the
-architecture covers all ports of the system, \ie $P = P_A$, we
-have $P\setminus P_A = \emptyset$ and the only interactions
-allowed in $A(\cB)$ are those belonging to $\Gamma$.  Notice also
-that the restrictions imposed by \defn{arch:application} on the
-set of operand components $\cB$ ensure that an interaction in
-$\IMextend{\Gamma}{P}$ can only refer to variables of the
-participating components.
-%
-Finally, the definition of $\IMextend{\Gamma}{P}$ requires that
+interaction.  %% In particular, they can join the interactions in
+%% $\Gamma$ (see \eq{im:extension}).  If the interface of the
+%% architecture covers all ports of the system, \ie $P = P_A$, we
+%% have $P\setminus P_A = \emptyset$ and the only interactions
+%% allowed in $A(\cB)$ are those belonging to $\Gamma$.  Notice also
+%% that the restrictions imposed by \defn{arch:application} on the
+%% set of operand components $\cB$ ensure that an interaction in
+%% $\IMextend{\Gamma}{P}$ can only refer to variables of the
+%% participating components.
+%
+%% Finally, 
+The definition of $\IMextend{\Gamma}{P}$ requires that
 an interaction from $\Gamma$ be involved in every interaction
@@
 
-\begin{example}
-  The architecture in \fig{schema:ArchFailure:BIP} enforces the
-  following properties:
-  \begin{enumerate}
-  \item There is always a possibility to reset the system after a
-    failure:
-    \begin{equation}
-      \label{eq:prop:reset:can}
-      \AG (\PortFail \rightarrow \EF \PortReset).
-    \end{equation}
-  \item Whenever a reset is requested, it will eventually be
-    effectuated:
-    \begin{equation}
-      \label{eq:prop:reset:will}
-      \AG (\PortAsk \rightarrow \AF \PortReset).
-    \end{equation}
-  \item As long as no failure has occured, the $z$ variable of the
-    $\NameTimer$ component has the value $\topinterval$:
-    \begin{equation}
-      \label{eq:prop:z:top}
-      \AW[\quad]{(z = \topinterval)}{\PortFail} \land\quad
-      \AG \bigl(
-      \PortReset \rightarrow \AW[]{(z = \topinterval)}{\PortFail}
-      \bigr).
-    \end{equation}
-  \item A reset can only be requested within the specified delay after
-    a failure:
-    \begin{multline}
-      \label{eq:prop:to:delay}
-      \forall T_0, T_1 \in \sZ,\
-      \AG \Big((\PortFail \land \NameTimer.t = T_0) \rightarrow
-      \\
-      \AW[]{\bigl((\PortAsk \land \NameTimer.t = T_1) \rightarrow
-        (T_1 - T_0 \in \NameCtrl.\mathit{zone})\bigr)
-      }{
-        (\PortReset \lor \PortResume)
-      }\Big),
-    \end{multline}
-    where $T_0$ and $T_1$ are integer parameters.  (The formula
-    holds with the universal quantification over $T_0$ and $T_1$
-    due to the fact that their individual values only appear in
-    the left-hand sides of the two implications.)
-  \end{enumerate}
-\end{example}
+In our running example, there are four dangling ports.  Intuitively, the
+architecture monitors the activation of the dangling port {\PortFail}, then
+waits for a period comprised between $\mathrm{Min}$ and $\mathrm{Max}$
+and, unless {\PortResume} is activated, asks for a system reset
+through an invocation of the dangling port {\PortAsk}.
 
@@
     \Gamma = \bsetdef{
-      (a, g^1 \land g^2, e^1 \expmix e^2) 
+      (a, g^1 \land g^2, u^1 \expmix u^2) 
     }{
-      (a \cap P_{A_i}, g^i, e^i) \in \Gamma_i,
+      (a \cap P_{A_i}, g^i, u^i) \in \Gamma_i,
       \text{ for } i = 1,2
@@
   \label{prop:arcomp:nice}
-  Architecture composition $\arcomp$ is commutative and
-  associative; it is idempotent if all coordinating components
-  are deterministic; $A_{id} = \bigl(\emptyset, \emptyset,
-  \emptyset, \emptyset, \{(\emptyset, \true, \noop)\}\bigr)$ is its neutral element, \ie for
-  any architecture $A$, we have $A \oplus A_{id} \arequiv A$.
-  Furthermore, for any component $B$, we have $A_{id}(B) = \mu(B)$.
+  %% Architecture composition
+  $\arcomp$ is associative and commutative.
+  %%; it is idempotent if all coordinating components
+  %% are deterministic; $A_{id} = \bigl(\emptyset, \emptyset,
+  %% \emptyset, \emptyset, \{(\emptyset, \true, \noop)\}\bigr)$ is its neutral element, \ie for
+  %% any architecture $A$, we have $A \oplus A_{id} \arequiv A$.
+  %% Furthermore, for any component $B$, we have $A_{id}(B) = \mu(B)$.
 \end{proposition}
@@
 \begin{proof}[Sketch of the proof]
-  Commutativity and associativity follow from the corresponding
+  %% Commutativity and associativity 
+  Follows from the corresponding
   properties of set union, Boolean conjunction and
-  \todoSB{Check ``semi''}\hl{semilattice meet}.
-%
-\todoLH{Check when equivalence is defined}
-  Suppose we have two architectures $A \arequiv A'$.  This does not
-  necessarily mean that their sets of coordinating components
-  coincide.  However, if all the involved coordinating components
-  are deterministic, then, in any state of $(A \arcomp A')(\cB)$,
-  both architectures will impose the same restrictions, enabling
-  the same interactions between the coordinating and operand
-  components.  Hence, we have $(A \arcomp A')(\cB) = A(\cB) =
-  A'(\cB)$.  Since this holds for any set of components $\cB$, we
-  conclude that $A \arcomp A' \arequiv A \arequiv A'$.
-%
-  The properties of $A_{id}$ follow immediately from the
-  definitions of architecture application and composition.
+  semilattice meet.
+%
+%% \todoLH{Check when equivalence is defined}
+%%   Suppose we have two architectures $A \arequiv A'$.  This does not
+%%   necessarily mean that their sets of coordinating components
+%%   coincide.  However, if all the involved coordinating components
+%%   are deterministic, then, in any state of $(A \arcomp A')(\cB)$,
+%%   both architectures will impose the same restrictions, enabling
+%%   the same interactions between the coordinating and operand
+%%   components.  Hence, we have $(A \arcomp A')(\cB) = A(\cB) =
+%%   A'(\cB)$.  Since this holds for any set of components $\cB$, we
+%%   conclude that $A \arcomp A' \arequiv A \arequiv A'$.
+%% %
+%%   The properties of $A_{id}$ follow immediately from the
+%%   definitions of architecture application and composition.
 \end{proof}
 
-The last statement of \prop{arcomp:nice} highlights a subtle point:
-$A_{id}$ is the neutral element of the $\arcomp$ operator\mdash it is
-not the identity operator on components.
+%% The last statement of \prop{arcomp:nice} highlights a subtle point:
+%% $A_{id}$ is the neutral element of the $\arcomp$ operator\mdash it is
+%% not the identity operator on components.
 
@@
 
-\begin{definition}[Safety properties]
+\begin{definition}[Properties]
   \label{defn:property}
-  Let $B$ be a component.  A \emph{safety property} (below,
-  simply \emph{property}) of $B$ is a state predicate $\Phi:
-  S_{\semopen{B}} \rightarrow \sB$, such that $\bigl((q,
+  Let $B$ be a component.  A \emph{(safety) property} 
+  of $B$ is a predicate $\Phi$ on
+  $S_{\semopen{B}}$, such that $\bigl((q,
   \val{}{}) \models \Phi\bigr) \land (\val[\primeit]{}{} \order
-  \val{}{})$ implies $(q, \val[\primeit]{}{}) \models \Phi$,
-  where we write $(q, \val{}{}) \models \Phi$ iff $\Phi(q,
-  \val{}{}) = \true$.  A property $\Phi$ is \emph{initial} if
+  \val{}{})$ implies $(q, \val[\primeit]{}{}) \models \Phi$.
+  %% ,
+  %% where we write $(q, \val{}{}) \models \Phi$ iff $\Phi(q,
+  %% \val{}{}) = \true$.
+  A property $\Phi$ is \emph{initial} if
   $s^0_{\semopen{B}} \models \Phi$.
@@
 
-\todoSB{Cite the original paper somewhere.}
+\addSB{Although we define properties as state predicates, any
+  appropriate logic can be used to specify them.  For instance, the
+  property \emph{``There is always a possibility to reset the system
+    after a failure''} enforced by the Failure Monitor architecture
+  can be specified using CTL as $\AG (\PortFail \rightarrow \EF
+  \PortReset)$.  Additional properties are provided in \app{properties}.}
+
+%% \todoSB{Cite the original paper somewhere.}
 The main idea of our approach is that an architecture enforces
@@
 \begin{definition}[Enforcing properties]
-  \label{defn:impose}
+  \label{defn:enforce}
   Let $A = \tuple{\cC, P_A, V_A, \export[A], \Gamma}$ be an architecture; let $\cB$
   be a set of components and $\Phi$ an initial property of
-  their parallel composition $A_{id}(\cB)$ (see
-  \prop{arcomp:nice}).  We say that \emph{$A$ enforces $\Phi$ on
+  their parallel composition $\Gamma_{\|}(\cB)$,
+  with $\Gamma_{\|} = \setdef{(a,\true,\emptyset)}{a \subseteq \bigcup_{B \in \cB} P_B}$.
+  We say that \emph{$A$ enforces $\Phi$ on
     $\cB$} iff, for every state $s = (s_c, s_b)$ reachable in
@@
 
-\begin{definition}[Upwards compatibility]
-  \label{defn:up:compat}
-  \todoSB{Summarise in English and move to the appendix}
-%
-  Consider two architectures $A_i = \tuple{\cC_i, V_{A_i}, P_{A_i},
-  \export[A_i], \Gamma_i}$, for $i = 1,2$.
-%
-  We say that $A_1$ and $A_2$ are \emph{upwards compatible} iff, for
-  any two interactions $(a_i, g_i, e_i) \in \Gamma_i$, such that $a_1
-  \cap P_{A_2} = a_2 \cap P_{A_1}$ (\ie they agree on the common ports
-  of the two architectures), we have 1)~for any interaction $(b_1,
-  h_1, f_1) \in \Gamma_1$, such that $a_1 \varsubsetneq b_1$, there
-  exists an interaction $(b_2, h_2, f_2) \in \Gamma_2$, such that $a_2
-  \subseteq b_2$, $b_1 \cap P_{A_2} = b_2 \cap P_{A_1}$ and the 
-  implication  
-%
-  \begin{multline*}
-    \left(
-    \exists (q^1_C)^{C \in \supp{b_1} \cap \cC_1}:
-    \exists (q^2_C)^{C \in \supp{a_2} \cap \cC_2}:
-    \bigwedge_{
-      \begin{multlined}
-        \scriptstyle
-        C \in \supp{b_1} \cap \cC_1 \cap
-        \\
-        \scriptstyle
-        \supp{a_2} \cap \cC_2
-      \end{multlined}
-    }
-    q^1_C = q^2_C
-    \ \land
-    \right.
-    \\
-    \begin{aligned}
-      \exists \bigl(q^1_C \goesto{b_1 \cap P_C, g^{b_1}_C, f^{b_1}_C}\bigr)^{C \in \supp{b_1} \cap \cC_1}:
-      & \quad \left.
-      h_1 \land \bigwedge_{C \in \supp{b_1} \cap \cC_1} g^{b_1}_C
-      \ \land \right.
-      \\
-      \exists \bigl(q^1_C \goesto{a_1 \cap P_C, g^{a_1}_C, e^{b_1}_C}\bigr)^{C \in \supp{a_1} \cap \cC_1}:
-      & \quad \left.
-      g_1 \land \bigwedge_{C \in \supp{a_1} \cap \cC_1} g^{a_1}_C
-      \ \land \right.
-      \\
-      \exists \bigl(q^2_C \goesto{a_2 \cap P_C, g^{a_2}_C, e^{a_2}_C}\bigr)^{C \in \supp{a_2} \cap \cC_2}:
-      & \quad
-      \left.
-      g_2 \land \bigwedge_{C \in \supp{a_2} \cap \cC_2} g^{a_2}_C
-      \right) \implies 
-    \end{aligned}
-  \end{multline*}
-%
-  \begin{multline*}
-    \left(
-    \exists (q^2_C)^{C \in (\supp{b_2}\setminus\supp{a_2}) \cap \cC_2}:
-            {\color{white}\bigwedge_{C \in \cC_1}}\right. % Fake bigwedge to make the parenthesis the right size
-            \\
-            \left.
-            \exists \bigl(q^2_C \goesto{b_2 \cap P_C, g^{b_2}_C, f^{b_2}_C}\bigr)^{C \in \supp{b_2} \cap \cC_2}:
-            h_2 \land
-            \bigwedge_{C \in \supp{b_2} \cap \cC_2} g^{b_2}_C
-            \right)
-  \end{multline*}
-%  
-  holds for all valuations $\val{}{1} : V_{A_1} \rightarrow \data$
-  and $\val{}{2} : V_{A_2} \rightarrow \data$; and 2)~symmetrically
-  for any interaction $(b_2, h_2, f_2) \in \Gamma_2$, such that $a_2
-  \varsubsetneq b_2$.
-\end{definition}
+\defn{up:compat} in \secn{arch:appendix} provides a formal definition
+of the notion of \emph{upwards compatibility}, which we present here
+informally due to page limitations.  Two architectures $A_1$ and $A_2$
+are said to be upwards compatible iff, whenever their composition
+involves the fusion of two interactions $a_1 = a \cap P_{A_1}$ and
+$a_2 = a \cap P_{A_2}$ (see \eq{arch:composition}), whereof one, say
+$a_1$, is inhibited in a given state by a larger interaction $b_1
+\supset a_1$, there exists an interaction $b_2 \supseteq a_2$ that can
+be fused with $b_1$ to form an interaction enabled in the same state.
 
@@
 We will define the encoding of BIP architectures into pNets by
-associating to each architecture \emph{and a partition of its dangling
-  ports} the corresponding pNet.  Notice that the addition of a
-partition of dangling ports is a matter of convenience, since one can
-use a trivial partition comprising only one complete set of dangling
-ports.
-
-Let $A = \tuple{\cC, V_A, P_A, \export[A], \Gamma}$ be an
-architecture.  For each $C \in \cC$, let $C = \tuple{Q_C, q^0_C, V_C,
-  \val{0}{C}, P_C, \export[C], \goesto{}}$.  Finally, let $\partition
-\subseteq 2^{P_A}$ be a partition of the set of dangling ports of $A$,
-\ie $\bigcup_{D \in \partition} D = P_A \setminus \bigcup_{C \in \cC}
-P_C$ and $D_1 \cap D_2 = \emptyset$, for any two distinct $D_1, D_2
-\in \partition$.  In particular, as mentioned above, one can consider
-the trivial partition $\partition \bydef{=} \{P_A \setminus \bigcup_{C
-  \in \cC} P_C\}$.
+associating to each architecture $A = \tuple{\cC, V_A, P_A,
+  \export[A], \Gamma}$ with $C = \tuple{Q_C, q^0_C, V_C, \val{0}{C},
+  P_C, \export[C], \goesto{}}$, for each $C \in \cC$, \emph{and a
+  partition $\partition \subseteq 2^{P_A}$ of its dangling ports} (\ie
+$\biguplus_{D \in \partition} D = P_A \setminus \bigcup_{C \in \cC}
+P_C$), the corresponding pNet $\nopri[A, \partition]$.
+%
+%% and $D_1 \cap D_2 = \emptyset$, for any two distinct $D_1, D_2
+%% \in \partition$.
+%
+%% Notice that this addition 
+%% is a matter of convenience, since one can
+%% use the trivial partition $\partition \bydef{=} \{P_A \setminus \bigcup_{C
+%%   \in \cC} P_C\}$.
 
@@
 implicitly involved in the definition of $\Gamma$.
-
-\paragraph{Encoding the coordinators} We define the
-mapping $\nopri$ as $\nopri[A, \partition] \bydef{=}
-\pNetTuple{(\nopri[C])^{C \in \cC}, \partition, \nopri[\Gamma]}$,
-where, for each $C \in \cC$, the encoding $\nopri[C]$ is a pLTS
-$\pNetTuple{S, s_0, \goesto[{\nopri[C]}]{}}$, such that
-%
-\begin{itemize}
-\item $s_0 \not\in Q_C$ is fresh and $S = Q_C \cup \{s_0\}$,
-\item $\vars(s) = V_C$, for all $s \in Q_C$, and $\vars(s_0) =
-  \emptyset$,
-\item the transition relation $\goesto[{\nopri[C]}]{}$ is defined as
-  the union of three sets of transitions:
-%
-  \begin{multline}
-    \label{eq:nopri:trans}
-    \goesto[{\nopri[C]}]{} \bydef{=}
-    \bsetdef{\tuple{s, a(\true), g, u, s'}}{
-      \tuple{s, a, g, u, s'} \in \goesto{}}
-    \\    
-    \cup
-    \bsetdef{\tuple{s, a(\false), \true, \noop, s}}{
-      s \in Q_C, a \in P_C}
-    \\
-    \cup
-    \bigl\{(s_0, \init, \true, \mathit{init}, q^0_C)\bigr\}
-    \,,
-  \end{multline}
-%
-  where $\mathit{init} = \bigl(x := \val{0}{C}(x)\bigr)^{x \in V_C}$.
-\end{itemize}
-
-Intuitively, we 1)~introduce a fresh initial state with an additional
+%
+We define $\nopri[A, \partition] \bydef{=} \pNetTuple{(\nopri[C])^{C
+    \in \cC}, \partition, \nopri[\Gamma]}$, where $\nopri[C]$ and
+$\nopri[\Gamma]$ are the encodings of a coordinator $C$ and the
+interaction model $\Gamma$ respectively.
+
+\paragraph{Encoding the coordinators}
+To encode a coordinator $C$, we 1)~introduce a fresh initial state with an additional
 $\init$ transition that initialises all the variables to those defined
@@
 $\false$.
+
+Formally,  $\nopri[C] \bydef{=} \pNetTuple{S, s_0, \goesto[{\nopri[C]}]{}}$, such that
+%
+\begin{itemize}
+\item $s_0 \not\in Q_C$ is fresh and $S = Q_C \cup \{s_0\}$,
+\item $\vars(s) = V_C$, for all $s \in Q_C$, and $\vars(s_0) =
+  \emptyset$,
+%% \item the transition relation $\goesto[{\nopri[C]}]{}$ is defined as
+%%   the union of three sets of transitions
+%%   (with $\mathit{init} \bydef{=} \bigl(x := \val{0}{C}(x)\bigr)^{x \in V_C}$):
+%% %
+%%   \begin{multline}
+%%     \label{eq:nopri:trans}
+%%     {\goesto[{\nopri[C]}]{}} \bydef{=}
+%%     \bsetdef{\tuple{s, a(\true), g, u, s'}}{
+%%       \tuple{s, a, g, u, s'} \in \goesto{}}
+%%     \\    
+%%     \cup
+%%     \bsetdef{\tuple{s, a(\false), \true, \noop, s}}{
+%%       s \in Q_C, a \in P_C}
+%%     %% \\
+%%     \cup
+%%     \bigl\{(s_0, \init, \true, \mathit{init}, q^0_C)\bigr\}
+%%     \,.
+%%   \end{multline}
+
+\item ${\goesto[{\nopri[C]}]{}} \bydef{=} T_1 \cup T_2 \cup T_3$, with
+  $T_1 = \bsetdef{\tuple{s, a(\true), g, u, s'}}{
+      \tuple{s, a, g, u, s'} \in \goesto{}}$,
+  $T_2 = \bsetdef{\tuple{s, a(\false), \true, \noop, s}}{
+      s \in Q_C, a \in P_C}$,
+  $T_3 = \bigl\{(s_0, \init, \true, \mathit{init}, q^0_C)\bigr\}$
+    and $\mathit{init} \bydef{=} \bigl(x := \val{0}{C}(x)\bigr)^{x \in V_C}$.
+\end{itemize}
 
@@
 have an associated Boolean value, nor the additional loop transitions.
-\todoSB{Revise this if necessary}\hl{We will explicitate this optimisation once we have defined the
+\todoSB{Revise this if necessary}\hl{We will explicitate this optimisation after we define the
 encoding of the interaction model.}
@@
   \centering
-  \includegraphics[width=\columnwidth]{FailureTimerPNET-v4}
+  \includegraphics[width=0.9\columnwidth]{FailureTimerPNET-v4}
   \caption{The open pNET encoding the Failure Monitor architecture (\fig{schema:ArchFailure:BIP}) without the priority model}
@@
 \paragraph{Encoding the interaction model}
-First of all, recall that $\nopri[A, \partition ] \bydef{=}
-\pNetTuple{(\nopri[C])^{C \in \cC}, \partition, \nopri[\Gamma]}$.
-Thus, the holes in the resulting pNet are indexed by the elements of
+%% First of all, recall that $\nopri[A, \partition ] \bydef{=}
+%% \pNetTuple{(\nopri[C])^{C \in \cC}, \partition, \nopri[\Gamma]}$.
+%% Thus, 
+The holes in $\nopri[A, \partition]$ are indexed by the elements of
 the partition \partition.  For the encoding of our running example, we
@@
 the actions provided by the ``environment'' (other components of the
-system) that are triggered in case of a persistent failure.  Similarly
-to the encoding of the coordinators, in the synchronisation vectors of
+system) that are invoked in case of a persistent failure.  As for
+the encoding of the coordinators, in the synchronisation vectors of
 \nopri[\Gamma], we will associate Boolean values to the actions
@@
 allowed interactions, depending on its hierarchical structure and the
-use of synchrons and triggers.  \noteSB{Move this to
-  \secn{components}?}For instance, the connector {\NameTimer.\PortTick
-  \trigsynch (\PortFail \trigsynch \NameCtrl.\PortFail)} is a
-two-level hierarchical connector.  In the second-level subconnector
-{\PortFail \trigsynch \NameCtrl.\PortFail}, the port {\PortFail} is a
-trigger, whereas {\NameCtrl.\PortFail} is a synchron.  Therefore, this
-subconnector allows two interactions: one with {\PortFail} alone and
-another one involving both ports.  Similarly, at the top level,
-{\NameTimer.\PortTick} is a trigger, whereas the second-level
-subconnector is a synchron.  Hence, the overall connector allows the
-interaction involving only one port {\NameTimer.\PortTick}\footnote{%
-%
-  Such interactions are called \emph{singleton interactions}.
-%
-} and any interaction involving both {\NameTimer.\PortTick} and
-\emph{some} interaction of the second-level subconnector.  Combining
-the two levels we can see that the entire connector defines the
-following three interactions (observe that $\topinterval +
-\NameTimer.t = \topinterval$ and $\NameTimer.z \cap \topinterval =
-\NameTimer.z$):
-%
-\begin{align*}
-  \bigl(\{\NameTimer.\PortTick\}&,
-  \true, 
-  \NameTimer.z := \NameTimer.z\bigr)
-  \,,\\
-  \bigl(\{\PortFail, \NameTimer.\PortTick\}&,
-  \true,
-  \NameTimer.z := \NameTimer.z\bigr)
-  \,,\\
-  \bigl(\{\NameCtrl.\PortFail, \PortFail, \NameTimer.\PortTick \}&,
-  \true,
-  \NameTimer.z := \NameTimer.z \cap (\NameCtrl.\mathit{zone} + \NameTimer.t)\bigr)
-  \,.\
-\end{align*}
+use of synchrons and triggers.
 
@@
 %
-  By \eq{im:sem} and \eq{priority:sem}, this implies
+  By \defn{im:sem} and \defn{priority:sem}, this implies
   that
@@
 %
-  is the conjunct encoding the maximal progress priority
-  \eq{priority:sem}.  As above for $g'$, for each $(b, h', f')$ in
+  is the conjunct encoding the maximal progress priority in
+  \defn{priority:sem}.  As above for $g'$, for each $(b, h', f')$ in
   \eq{onestep:maxprog:guard}, $h'$ can be decomposed as $h' = h \land
@@
   %% Denoting $P_\cB = \bigcup_{B \in \supp{a} \cap \cB} P_B$, 
-  By \eq{im:sem}, we have
+  By \defn{im:sem}, we have
 %
@@
 
-  By \eq{comp:semantics} and \eq{im:sem}, we have
+  By \defn{comp:semantics} and \defn{im:sem}, we have
   $
@@
 
-\subsection{Full results of the case study}
+\section{Additional material for the theory of architectures}
+\label{secn:arch:appendix}
+
+\begin{definition}[Upwards compatibility]
+  \label{defn:up:compat}
+  \todoSB{Summarise in English and move to the appendix}
+%
+  Consider two architectures $A_i = \tuple{\cC_i, V_{A_i}, P_{A_i},
+  \export[A_i], \Gamma_i}$, for $i = 1,2$.
+%
+  We say that $A_1$ and $A_2$ are \emph{upwards compatible} iff, for
+  any two interactions $(a_i, g_i, e_i) \in \Gamma_i$, such that $a_1
+  \cap P_{A_2} = a_2 \cap P_{A_1}$ (\ie they agree on the common ports
+  of the two architectures), we have 1)~for any interaction $(b_1,
+  h_1, f_1) \in \Gamma_1$, such that $a_1 \varsubsetneq b_1$, there
+  exists an interaction $(b_2, h_2, f_2) \in \Gamma_2$, such that $a_2
+  \subseteq b_2$, $b_1 \cap P_{A_2} = b_2 \cap P_{A_1}$ and the 
+  implication  
+%
+  \begin{multline*}
+    \left(
+    \exists (q^1_C)^{C \in \supp{b_1} \cap \cC_1}:
+    \exists (q^2_C)^{C \in \supp{a_2} \cap \cC_2}:
+    \bigwedge_{
+      \begin{multlined}
+        \scriptstyle
+        C \in \supp{b_1} \cap \cC_1 \cap
+        \\
+        \scriptstyle
+        \supp{a_2} \cap \cC_2
+      \end{multlined}
+    }
+    q^1_C = q^2_C
+    \ \land
+    \right.
+    \\
+    \begin{aligned}
+      \exists \bigl(q^1_C \goesto{b_1 \cap P_C, g^{b_1}_C, f^{b_1}_C}\bigr)^{C \in \supp{b_1} \cap \cC_1}:
+      & \quad \left.
+      h_1 \land \bigwedge_{C \in \supp{b_1} \cap \cC_1} g^{b_1}_C
+      \ \land \right.
+      \\
+      \exists \bigl(q^1_C \goesto{a_1 \cap P_C, g^{a_1}_C, e^{b_1}_C}\bigr)^{C \in \supp{a_1} \cap \cC_1}:
+      & \quad \left.
+      g_1 \land \bigwedge_{C \in \supp{a_1} \cap \cC_1} g^{a_1}_C
+      \ \land \right.
+      \\
+      \exists \bigl(q^2_C \goesto{a_2 \cap P_C, g^{a_2}_C, e^{a_2}_C}\bigr)^{C \in \supp{a_2} \cap \cC_2}:
+      & \quad
+      \left.
+      g_2 \land \bigwedge_{C \in \supp{a_2} \cap \cC_2} g^{a_2}_C
+      \right) \implies 
+    \end{aligned}
+  \end{multline*}
+%
+  \begin{multline*}
+    \left(
+    \exists (q^2_C)^{C \in (\supp{b_2}\setminus\supp{a_2}) \cap \cC_2}:
+            {\color{white}\bigwedge_{C \in \cC_1}}\right. % Fake bigwedge to make the parenthesis the right size
+            \\
+            \left.
+            \exists \bigl(q^2_C \goesto{b_2 \cap P_C, g^{b_2}_C, f^{b_2}_C}\bigr)^{C \in \supp{b_2} \cap \cC_2}:
+            h_2 \land
+            \bigwedge_{C \in \supp{b_2} \cap \cC_2} g^{b_2}_C
+            \right)
+  \end{multline*}
+%  
+  holds for all valuations $\val{}{1} : V_{A_1} \rightarrow \data$
+  and $\val{}{2} : V_{A_2} \rightarrow \data$; and 2)~symmetrically
+  for any interaction $(b_2, h_2, f_2) \in \Gamma_2$, such that $a_2
+  \varsubsetneq b_2$.
+\end{definition}
+
+\section{Additional material for the case study}
+
+\subsection{Properties enforced by the Failure Monitor architecture}
+\label{secn:properties}
+
+The architecture in \fig{schema:ArchFailure:BIP} enforces the
+following safety properties:
+\begin{enumerate}
+\item There is always a possibility to reset the system after a
+  failure:
+  \begin{equation}
+    \label{eq:prop:reset:can}
+    \AG (\PortFail \rightarrow \EF \PortReset).
+  \end{equation}
+
+\item As long as no failure has occured, the $z$ variable of the
+  $\NameTimer$ component has the value $\topinterval$:
+  \begin{equation}
+    \label{eq:prop:z:top}
+    \AW[\quad]{(z = \topinterval)}{\PortFail} \land\quad
+    \AG \bigl(
+    \PortReset \rightarrow \AW[]{(z = \topinterval)}{\PortFail}
+    \bigr).
+  \end{equation}
+
+\item A reset can only be requested within the specified delay after
+  a failure:
+  \begin{multline}
+    \label{eq:prop:to:delay}
+    \forall T_0, T_1 \in \sZ,\
+    \AG \Big((\PortFail \land \NameTimer.t = T_0) \rightarrow
+    \\
+    \AW[]{\bigl((\PortAsk \land \NameTimer.t = T_1) \rightarrow
+      (T_1 - T_0 \in \NameCtrl.\mathit{zone})\bigr)
+    }{
+      (\PortReset \lor \PortResume)
+    }\Big),
+  \end{multline}
+  where $T_0$ and $T_1$ are integer parameters.  (The formula
+  holds with the universal quantification over $T_0$ and $T_1$
+  due to the fact that their individual values only appear in
+  the left-hand sides of the two implications.)
+\end{enumerate}
+
+In addition\mdash although outside the scope of this paper\mdash it
+enforces the \emph{liveness} property \emph{``Whenever a reset is
+  requested, it will eventually be effectuated''}:
+%
+  \begin{equation}
+    \label{eq:prop:reset:will}
+    \AG (\PortAsk \rightarrow \AF \PortReset).
+  \end{equation}
+%
+  (See \cite{AttieBBJS16-architectures-faoc} for the definition and
+  results on the preservation of liveness properties by composition of
+  architectures in absence of data and priorities.)
+
+\subsection{Output of the open-automaton construction}
 \label{secn:full-results}
 
-\subsubsection{Output of the open-automaton construction}
 The standard pretty-print of OTs by the tool include the transitions

### 2019-01-25 2018-Arch-pNets/arch-pNets.tex
new figures 2 et 3
4.1 et listing/OTs

@@
 
+%% \begin{figure}[t]
+%%   \centering
+%%   \includegraphics[width=\columnwidth]{TimerOpenAut}
+%%   \caption{The open Automaton of the Failure Monitor Architecture}
+%%   \label{schema:ArchFailure:BIP}
+%% \end{figure}
+
 \begin{figure}[t]
   \centering
-  \includegraphics[width=\columnwidth]{TimerOpenAut}
+  \includegraphics[width=0.8\columnwidth]{TimerOADetailed}
   \caption{The open Automaton of the Failure Monitor Architecture}
@@
 
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=0.8\columnwidth]{FailureTimerOA}
-  \caption{The open Automaton of the Failure Monitor Architecture}
-  \label{schema:ArchFailure:BIP}
-\end{figure}
-
-12 open transitions... Comments on the predicates ???
-
-Should list some temporal logic properties....
+In Figure~\ref{schema:ArchFailure:OA} we show the full open automaton
+obtained from our pNet. For reasons of space, we have not shown the
+detail of the open transition, but only the assignement of state
+variables, and the resulting action. You can find the full details in
+Appendix \ref{secn:full-results}. As an example, $OT_3$ is the one explained in Example
+\ref{Example:TimerOT3} page \pageref{Example:TimerOT3}
+
+\todoEM{12 open transitions... Comments on the predicates ???}
 
@@
 
-INFO  BIPArchFailureTimerMax_LTF3 -
        {t0---init-->t1, s0---init-->s1},   {},  [true],
@@
     OT1 ------------------------------------------------------------
-        <t0_s0>-----alpha4----><t1_s1>
-
-INFO  BIPArchFailureTimerMax_LTF3 -
+        <t0_s0>-----init----><t1_s1>
+
        {t1---tick(z, t, z1)-->t1, s1---fail(zone, false)-->s1},   {---:hb_B-->},
@@
     OT2 ------------------------------------------------------------
-        <t1_s1>-----alpha0----><t1_s1>
-
-INFO  BIPArchFailureTimerMax_LTF3 -
+        <t1_s1>-----fail----><t1_s1>
+
        {t1---tick(z, t, z1)-->t1, s1---fail(zone, true)-->s2},   {---:hb_B-->},
@@
     OT3 ------------------------------------------------------------
-        <t1_s1>-----alpha0----><t1_s2>
-
-INFO  BIPArchFailureTimerMax_LTF3 -
+        <t1_s1>-----fail----><t1_s2>
+
        {t1---cancel(false)-->t1, s1---resume(false)-->s1},   {---:hb_B-->},
@@
     OT4 ------------------------------------------------------------
-        <t1_s1>-----alpha1----><t1_s1>
-
-INFO  BIPArchFailureTimerMax_LTF3 -
+        <t1_s1>-----resume----><t1_s1>
+
        {t1---timeout-->t1, s1---timeout-->s1},   {---:hb_E-->},
@@
     OT5 ------------------------------------------------------------
-        <t1_s1>-----alpha2----><t1_s1>
-
-INFO  BIPArchFailureTimerMax_LTF3 -
+        <t1_s1>-----ask----><t1_s1>
+
        {t1---tick(z, t, z1)-->t1, s2---fail(zone, false)-->s2},   {---:hb_B-->},
@@
     OT6 ------------------------------------------------------------
-        <t1_s2>-----alpha0----><t1_s2>
-
-INFO  BIPArchFailureTimerMax_LTF3 -
+        <t1_s2>-----fail----><t1_s2>
+
        {t1---cancel(false)-->t1, s2---resume(false)-->s2},   {---:hb_B-->},
@@
     OT7 ------------------------------------------------------------
-        <t1_s2>-----alpha1----><t1_s2>
-
-INFO  BIPArchFailureTimerMax_LTF3 -
+        <t1_s2>-----resume----><t1_s2>
+
        {t1---cancel(true)-->t1, s2---resume(true)-->s1},   {---:hb_B-->},
@@
     OT8 ------------------------------------------------------------
-        <t1_s2>-----alpha1----><t1_s1>
-
-INFO  BIPArchFailureTimerMax_LTF3 -
+        <t1_s2>-----resume----><t1_s1>
+
        {t1---timeout-->t1, s2---timeout-->s3},   {---:hb_E-->},
@@
     OT9 ------------------------------------------------------------
-        <t1_s2>-----alpha2----><t1_s3>
-
-INFO  BIPArchFailureTimerMax_LTF3 -
+        <t1_s2>-----ask----><t1_s3>
+
        {t1---tick(z, t, z1)-->t1, s3---fail(zone, false)-->s3},   {---:hb_B-->},
@@
     OT10 ------------------------------------------------------------
-        <t1_s3>-----alpha0----><t1_s3>
-
-INFO  BIPArchFailureTimerMax_LTF3 -
+        <t1_s3>-----fail----><t1_s3>
+
        {t1---cancel(false)-->t1, s3---resume(false)-->s3},   {---:hb_B-->},
@@
     OT11 ------------------------------------------------------------
-        <t1_s3>-----alpha1----><t1_s3>
-
-INFO  BIPArchFailureTimerMax_LTF3 -
+        <t1_s3>-----resume----><t1_s3>
+
         {s3---reset-->s1},   {---:hb_E-->},     [(:hb_E=ask)],   {}
     OT12 ------------------------------------------------------
-        <t1_s3>-----alpha3----><t1_s1>
-
-INFO  BIPArchFailureTimerMax_LTF3 - Total: 12 SATISFIABLE OTs
-INFO  BIPArchFailureTimerMax_LTF3 -        235 UNSATISFIABLE OTs
-INFO  BIPArchFailureTimerMax_LTF3 - Total Time: 1293 ms
+        <t1_s3>-----reset----><t1_s1>
+
+INFO  BIPArchFailureTimerMax - Total: 12 SATISFIABLE OTs
+INFO  BIPArchFailureTimerMax -        235 UNSATISFIABLE OTs
+INFO  BIPArchFailureTimerMax - Total Time: 1293 ms
 \end{verbatim}

### 2019-01-26 2018-Arch-pNets/arch-pNets.tex
arch-pNets paper: updated the safety property of the Failure Monitor architecture to There is always a possibility to reset the system or or resume operation after a single failure AG 􏰁(fil → E [¬fail U (resume ∨ reset)]])

@@
 \newcommand{\AW}[3][\ ]{\ensuremath{\mathtt{A}\left[#2\ \mathtt{W}\ #3\right]#1}}
+\newcommand{\EU}[3][\ ]{\ensuremath{\mathtt{E}\left[#2\ \mathtt{U}\ #3\right]#1}}
 
@@
   property \emph{``There is always a possibility to reset the system
-    after a failure''} enforced by the Failure Monitor architecture
-  can be specified using CTL as $\AG (\PortFail \rightarrow \EF
-  \PortReset)$.  Additional properties are provided in \app{properties}.}
+    or resume operation after a single failure'' (\ie without
+    additional failures occuring in the meantime)} enforced by the
+  Failure Monitor architecture can be specified using CTL as $\AG
+  \bigl(\PortFail \rightarrow \EU[]{\lnot \PortFail}{(\PortResume \lor
+    \PortReset)}\bigr)$.  Additional properties are provided in
+  \app{properties}.}
 
@@
 \begin{enumerate}
-\item There is always a possibility to reset the system after a
-  failure:
+\item There is always a possibility to reset the system or resume
+  operation after a single failure (\ie without additional failures
+  occuring in the meantime):
   \begin{equation}
     \label{eq:prop:reset:can}
-    \AG (\PortFail \rightarrow \EF \PortReset).
+    \AG \bigl(\PortFail \rightarrow \EU[]{\lnot \PortFail}{(\PortResume \lor \PortReset)}\bigr).
   \end{equation}

### 2019-01-27 2018-Arch-pNets/arch-pNets.tex
arch-pNets paper: (Minor) Edits to the example of an open transition

@@
 
-\begin{example}\emph{An open-transition.}
+\begin{example}[An open-transition]
   \label{OT:enable-composed}
-  The \texttt{Failure TimerMonitor} pNet of \Fig{FailureTimer:pNet} has 2 controllers 
-  and 2 holes. One of its possible open-transitions is:\\[-2ex]
+  The \texttt{Failure TimerMonitor} pNet of \Fig{FailureTimer:pNet} has \replaceSB{2 controllers 
+  and 2 holes.
+O}{two coordinators and four dangling ports, which can be grouped into two holes (see \secn{encoding} below).
+Disregarding the maximal progress priority, o}ne of its possible open-transitions is:\\[-2ex]
 %%   \footnote{Note the underlined action notation that we use to represent synchronised actions, i.e.
@@
 
-It correspond to the firing of the connector
-$''tick, fail, fail''$.
-It states that, if the hole B performs an action $fail$, and the (complex) guard is satisfied, then the variable $z$ is set to $z1$ (as specified by the guard), then the transition below the dotted line occurs and a global action labelled $\alpha_0$ occurs.
+It corresponds to the firing of the \replaceSB{connector
+$''tick, fail, fail''$}{interaction $\listset{\NameTimer.\PortTick, \PortFail, \NameCtrl.\PortFail}$}.
+It states that, if the hole $B$ performs an action $fail$, and the (complex) guard is satisfied, then the variable $z$ is set to $z1$ (as specified by the guard), then the transition below the dotted line occurs and a global action labelled $\alpha_0$ occurs.
 Only the second pLTS performs a transition from state $1$ to state $2$.

### 2019-01-28 2018-Arch-pNets/arch-pNets.tex
arch-pNets paper: Updated the encoding to include primed variables and update expressions

@@
   {\{B\mapsto fail(b0)\},\\
-    t<GetMax(z) \land b1=true \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),
-    \{z:=z1\} }
+    t<GetMax(z) \land b1=true \land b1=>b0 \land z'= (z \cap (b1?zone;TopInt)+t) {\color{blue}\land (t' = t) \land (zone' = zone)},\\
+    \{z:=z', {\color{blue}t := t'+1, zone := zone'}\} }
   {\ostate{11} \OTarrow{\alpha_0} \ostate{12}}
@@
 by the initial valuation $\val{0}{C}$ of $C$, 2)~define a pNet action algebra that associates, as action parameter, an
-additional Boolean value to each port, 3)~create pNet transitions that reflect the original transitions of
-$C$ with $\true$ as parameter and 4)~create additional loop transitions marked by
+additional Boolean value to each port, \add{3)~for each exported variable $x$, create the corresponding fresh variable $x'$ to allow updates during interactions,} 4)~create pNet transitions that reflect the original transitions of
+$C$ with $\true$ as parameter and 5)~create additional loop transitions marked by
 $\false$.
@@
 \item $s_0 \not\in Q_C$ is fresh and $S = Q_C \cup \{s_0\}$,
-\item $\vars(s) = V_C$, for all $s \in Q_C$, and $\vars(s_0) =
+\item $\vars(s) = V_C \cup \setdef{x'}{x \in \export[C](p), p \in a, s\goesto{a} }$, for all $s \in Q_C$, and $\vars(s_0) =
   \emptyset$,
@@
 
-\item ${\goesto[{\nopri[C]}]{}} \bydef{=} T_1 \cup T_2 \cup T_3$, with
-  $T_1 = \bsetdef{\tuple{s, a(\true), g, u, s'}}{
-      \tuple{s, a, g, u, s'} \in \goesto{}}$,
-  $T_2 = \bsetdef{\tuple{s, a(\false), \true, \noop, s}}{
-      s \in Q_C, a \in P_C}$,
-  $T_3 = \bigl\{(s_0, \init, \true, \mathit{init}, q^0_C)\bigr\}$
-    and $\mathit{init} \bydef{=} \bigl(x := \val{0}{C}(x)\bigr)^{x \in V_C}$.
+\item denoting  $\mathit{init} \bydef{=} \bigl(x := \val{0}{C}(x)\bigr)^{x \in V_C}$;
+  \noteSB{Ludo, Eric, pourriez-vous v\'erifier que cela est compr\'ehensible ?}%
+  \add{for $s \goesto{a, g, u} s'$ with $u = (x := e_x)^{x
+    \in V}$ (for some $V \subseteq V_C$),
+%  
+  $u' \bydef{=}
+  \bigl(x := e_x\bigr)^{x \in V \setminus \export[C](a)}
+  \cup
+  \bigl(x := e_x\bigl[\nicefrac{x'}{x}\bigr]\bigr)^{x \in V \cap \export[C](a)}$,
+%
+  and $\export[C]'(a) \bydef{=} \setdef{x'}{x \in \export[C](p), p \in a}$,
+%
+  \begin{multline*}
+    {\goesto[{\nopri[C]}]{}} \bydef{=} 
+    \Setdef{\Tuple{s, a\bigl(\export[C](a), \export[C]'(a),\true\bigr), g, u', s'}}{
+      s \goesto{a, g, u} s'}
+    \\
+    {} \cup
+    \Setdef{\Tuple{s, a\bigl(\export[C](a), \export[C]'(a),\false\bigr), \true, \noop, s}}{
+      s \in Q_C, \exists s' \in Q_C: s' \goesto{a}}
+    \\
+    {} \cup \bigl\{(s_0, \init, \true, \mathit{init}, q^0_C)\bigr\}.
+  \end{multline*}}
 \end{itemize}
@@
   \label{fig:FailureTimer:pNet}
+%
+  \noteSBin{The updated encoding exports more primed variables in the
+    actions, \eg $tick(z,t,z',t')$ and $fail(zone, zone', b1)$ instead
+    of $tick(z,t,z')$ and $fail(zone, b1)$, and SVs, \eg $\dots \land
+    (t' = t) \land (zone' = zone)$ in the guard of SV0. Shall we
+    update the figure to include these or, rather, explain that the
+    figure is cleaned-out for readability?}
+%
 \end{figure}
@@
   The other factor might be the facility of maximal progress
-  encoding\mdash TBC.  Traceability.  Anything else?
+  encoding\mdash TBC.  Traceability.  Anything else?\newline
+  \hl{UPDATE: Maximal progress encoding requires this!}
 %
@@
 
-In order to encode these interactions using only one synchronisation vector, we use
+\todoSB{Update?}\hl{In order to encode these interactions using only one synchronisation vector}, we use
 the additional Boolean values associated to each port by the encoding
-of coordinator components.  We observe that the three ports in this
-connector form a ``causality chain'': {\NameCtrl.\PortFail} can only
+of coordinator components.  For example, observe that the three ports in 
+the connector
+{\NameTimer.\PortTick
+  \trigsynch (\PortFail \trigsynch \NameCtrl.\PortFail)}
+form a ``causality chain'': {\NameCtrl.\PortFail} can only
 participate in the interaction if the dangling port {\PortFail}
@@
 The conjunction of these two implications can be used as a guard for
-the synchronisation vector encoding connector {\NameTimer.\PortTick
-  \trigsynch (\PortFail \trigsynch \NameCtrl.\PortFail)}.
+the synchronisation vector encoding this connector.
 
@@
 action name.  The guard $b_1 \Rightarrow b_0$ encodes the causal
-relation among ports {\NameCtrl.\PortFail} and {\PortFail}.  Notice
+relation between ports {\NameCtrl.\PortFail} and {\PortFail}.  Notice
 that, in our encoding, all three ports are present in the
@@
 representations of the connectors in \fig{schema:ArchFailure:BIP} are
-shown in \tab{connectors}.
+shown in \tab{connectors} (elements shown in red can be removed for
+simplification as described in the example above).
 
@@
 architecture $A$ and by $P_x$ the set of ports involved in the
-connector $x \in \gamma$.  Then, we have
-\begin{align*}
-  \gamma &=
-  \setdef{(x, g, u)}{x \in \ac(P_x), g \in \guards{V_x}, u \in
-    \assigns{V_x}}
-  \\
-  &\simeq \setdef{(a,g,u)}{(x,g,u) \in \gamma, a \in \intsem{x}}
-  = \Gamma
-  \,.
-\end{align*}
-
-We first define the encoding of $\Gamma$ as $\nopri[\Gamma] \bydef{=}
+connector $x \in \gamma$.  Then, \addSB{the interaction model defined by $\gamma$ is 
+  $\Gamma = \setdef{(a,g,u)}{(x,g,u) \in \gamma, a \in \intsem{x}}$
+  and the encoding of $\Gamma$ is} $\nopri[\Gamma] \bydef{=}
 \setdef{\nopri[x,g,u]}{(x,g,u) \in \gamma}$, where $\nopri[x,g,u]$ is the synchronisation vector defined by
 %
-\begin{equation}
+\begin{multline}
   \label{eq:nopri:connector}
   \nopri[x,g,u] \bydef{=}
-  \bigl(p(b_p,\export[A](p))\bigr)^{p \in P_x}
+  \Tuple{p\bigl(\export[A](p),{{\color{blue}\export[A]'(p),}}b_p\bigr)}^{p \in P_x}
   \rightarrow
   \alpha_p
-  \left[\bigwedge R(\tau(x))\bigl[\nicefrac{b_p}{p}\bigr]\right]
+  \\
+  \left[
+    \bigwedge R(\tau(x))\bigl[\nicefrac{b_p}{p}\bigr]
+    {\color{blue}{}
+    \land
+    \bigwedge_{(x := e_x) \in u} (x' = e_x)
+    \land
+    \bigwedge_{x \in \export[A](x), x \not\in u} (x' = x)
+    }
+    \right]
   \,,
-\end{equation}
+\end{multline}
+\noteSB{Ought to group ports by components in
+  $\Tuple{p\bigl(\export[A](p),\export[A]'(p),b_p\bigr)}^{p \in P_x}$...
+  \newline
+  Will probably restrict interactions to one port per component
+  throughout the paper to simplify.
+}
 %
@@
 
-\todoLHin{The update assignment is missing from the above encoding.
-  It should be $u\bigl[\nicefrac{b_p}{p}\bigr]$, but I do not see in
-  \defn{pnets} where should I place it.  I think it is missing there.
-  \Simon}
-
 \begin{theorem}
   The open automaton $\semopen{\nopri[A,\partition]}$ corresponding to
-  $\nopri[A,\partition]$ (see \defn{operationalSemantics}) is
+  $\nopri[A,\partition]$ is
   isomorphic to the LTS $\semopen{\Gamma\bigl(\cC_A, (B_D)^{D \in
@@
     V_D, \val{0}{D}, D, \export[D], \goesto{}}$, with
+  a fresh state $q$ and
+
 %
@@
     &\export[D](p) &= \export[A](p), \text{ for all $p \in D$}
-    \,,
+    \,.
   \end{align*}
 %
-  and $q$ a fresh state.
 \end{theorem}
@@
 \begin{proof}[Sketch of a proof]
+  \noteSB{This theorem is very probably correct: the key question is
+  whether isomorphism is, indeed, the relation to use. In absence of
+  silent transitions, must be the case.}
   The theorem follows from the correctness of $\tau$ and $R$ shown in
@@
 
-\noteSBin{This theorem is very probably correct: the key question is
-  whether isomorphism is, indeed, the relation to use. In absence of
-  silent transitions, must be the case.}
-
+\todoSB{This repeats things that were already said before.  Will reduce.}
 Observe now that this encoding can be optimised to remove unnecessary
@@
 (see \defn{arch:composition}).
+
+\todoSBin{Complete this section}
 

### 2019-01-29 2018-Arch-pNets/arch-pNets.tex
encore un pb de synchro ?

--- 2019-01-26 2018-Arch-pNets/arch-pNets.tex
@@
 \newcommand{\AW}[3][\ ]{\ensuremath{\mathtt{A}\left[#2\ \mathtt{W}\ #3\right]#1}}
-\newcommand{\EU}[3][\ ]{\ensuremath{\mathtt{E}\left[#2\ \mathtt{U}\ #3\right]#1}}
 
@@
   property \emph{``There is always a possibility to reset the system
-    or resume operation after a single failure'' (\ie without
-    additional failures occuring in the meantime)} enforced by the
-  Failure Monitor architecture can be specified using CTL as $\AG
-  \bigl(\PortFail \rightarrow \EU[]{\lnot \PortFail}{(\PortResume \lor
-    \PortReset)}\bigr)$.  Additional properties are provided in
-  \app{properties}.}
+    after a failure''} enforced by the Failure Monitor architecture
+  can be specified using CTL as $\AG (\PortFail \rightarrow \EF
+  \PortReset)$.  Additional properties are provided in \app{properties}.}
 
@@
 
+\begin{indent}
+  description courte et intuitive avec reference au papier d'Avocs
+\end{indent}
+
 %****************************************************************
@@
 \begin{enumerate}
-\item There is always a possibility to reset the system or resume
-  operation after a single failure (\ie without additional failures
-  occuring in the meantime):
+\item There is always a possibility to reset the system after a
+  failure:
   \begin{equation}
     \label{eq:prop:reset:can}
-    \AG \bigl(\PortFail \rightarrow \EU[]{\lnot \PortFail}{(\PortResume \lor \PortReset)}\bigr).
+    \AG (\PortFail \rightarrow \EF \PortReset).
   \end{equation}

### 2019-01-29 2016-Weak-FH-Bisim/WeakBisim.tex

--- 2019-01-07 2016-Weak-FH-Bisim/WeakBisim.tex
@@
     {
-       \set{(\beta^1_p)},\Pred^1_p,\Post^1_p   }
-         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$
-~and~ $\forall i \in [0\ldots m_2] \,\, P[Q]_{j_0}\!\models \openrule
-         {
-           \set{(\beta^3_p)},\Pred\,^3_p, \Post_p^3   }
-         {\ostate{u^{l\in L}_{pl}} \OTarrow {\tau} \ostate{u^{l\in L}_{(p+1)l}}}
-$\\
-and $ P[Q]_{j_0}	\models \openrule
+       (\set{\beta^1_p}),\Pred^1_p,\Post^1_p   }
+         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$,  $\qquad  P[Q]_{j_0}	\models \openrule
          {
@@
 $ 
-
+\\
+and 
+ $\forall p \in [0\ldots m_2] \,\, P[Q]_{j_0}\!\models \openrule
+         {
+           (\set{\beta^3_p}),\Pred\,^3_p, \Post_p^3   }
+         {\ostate{u^{l\in L}_{pl}} \OTarrow {\tau} \ostate{u^{l\in L}_{(p+1)l}}}
+$\\
 where for all $l\in L$:\\
@@
 \Post=(\bigotimes_{i=0}^{m_2}\Post^3_i)\subst{\Post^2}\bigotimes_{i=0}^{m_1}\subst{\Post^1_i}
-$
-
+$\\
 We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$:
@@
     {
-       \set{(\beta^1_p)},\Pred^1_p,\Post^1_p   }
+       (\set{\beta^1_p}),\Pred^1_p,\Post^1_p   }
          {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$ \\
@@
 			{
-				(\beta_{p})_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
-				{\Pred_p}\!\!',  
-				{\Post_p}\!\!'}
+				(\beta^1_{p})_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
+				{\Pred^1_p}\!',  
+				{\Post^1_p}\!'}
 			{\ostate{s_{p l}^{l\in L\setminus L_Q}} \OTarrow {\tau}
@@
 			{
-				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
-				{{\Post_p}\!\!''}}
+				(\beta^1_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred^1_p}\!''},  
+				{{\Post^1_p}\!''}}
 				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
@@
 
-such that  $\Pred^1_p \iff {\Pred_p}\!\!'
-		\land {\Pred_p}\!\!''\land \alpha_p=\beta_{pj_0}$, $\Post^1_p={\Post_p}\!\!'\uplus 
-		{\Post_p}\!\!''$ where ${{\Post_p}\!\!''}$ is the restriction of $\Post^1_p$ over variables of $\Leaves(Q)$.\\
-Else $Q$ does not move and \\
+such that  $\Pred^1_p \iff {\Pred^1_p}\!'
+		\land {\Pred^1_p}\!''\land \alpha_p=\beta_{pj_0}$, $\Post^1_p={\Post^1_p}\!'\uplus 
+		{\Post^1_p}\!''$ where ${{\Post^1_p}\!''}$ is the restriction of $\Post^1_p$ over variables of $\Leaves(Q)$.\\
+Else $Q$ does not move and we have: \\
 $P\models{\openrule
 			{
-				(\beta_{p})_j^{j\in (J\setminus \Holes(Q)) }, 
-				{\Pred^1_p},  
-				{\Post^1_p}}
+				(\beta^1_{p})_j^{j\in (J\setminus \Holes(Q)) }, 
+				{\Pred^1_p}\!',  
+				{\Post^1_p}\!'}
 			{\ostate{(s_{p l})^{l\in L\setminus L_Q}} \OTarrow {\tau}
@@
 
-\item Similarly for tau transitions on states named $u$.
-
-\item And, for the open transition $\symb{OT}$ in the form: $P[Q]_{j_0}	\models \openrule
+\item Similarly, we use the same process on states named $u$.
+
+\item Finally, for the open transition $\symb{OT}$ in the form: $P[Q]_{j_0}	\models \openrule
          {
@@
 			{
-				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
-				{\Pred}\,',  
-				{\Post}\,'}
+				(\beta^2)_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
+				{\Pred^2}',  
+				{\Post^2}'}
 			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
@@
 			{
-				\beta_j^{j\in J\cap\Holes(Q)}, {\Pred}\,'',  
-				{\Post}\,''}
+				(\beta^2)_j^{j\in J\cap\Holes(Q)}, {\Pred^2}'',  
+				{\Post^2}''}
 			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'}
@@
 such that  $\Pred^2 \iff {\Pred}\,'
-		\land {\Pred}\,''\land \alpha'=\beta_{j_0}$, $\Post^2={\Post}\,'\uplus 
-		{\Post}\,''$ where ${\Post}\,''$ is the restriction of $\Post^2$ over variables of $\Leaves(Q)$.
+		\land {\Pred^2}''\land \alpha'=\beta_{j_0}$, $\Post^2={\Post^2}'\uplus 
+		{\Post^2}''$ where ${\Post^2}''$ is the restriction of $\Post^2$ over variables of $\Leaves(Q)$.
 
@@
 \end{enumerate}
-
-By using  Lemma \ref{lem-rel-OT-WOT} we can conclude from case 1 and 2 that we have:
+By using  Lemma \ref{lem-rel-OT-WOT} we can conclude from cases 1, 2 and 3 that we have:
 \begin{mathpar}
@@
 \end{mathpar}
-
-\TODO{We will add side conditions ?? }\\
+where for all $l\in L$:\\
+$s_l=s_{0l} \wedge s_{{(m_1+1)}l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)}l=s'_l$\\
+$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\},\quad
+\displaystyle{\gamma_j}=\mybigdotcup_{i=0}^{m_1}  (\beta^1_{ij}) \dotcup  (\set{\beta^2}_i) \dotcup \mybigdotcup_{i=0}^{m_2} (\beta^3_{ij})
+\\
+\Pred\,'=\bigwedge_{i=0}^{m_1}
+{\Pred_i^1}'\land{\Pred^2}'\bigotimes_{i=0}^{m_1}\subst{{\Post_i^1}'}\land (\bigwedge_{i=0}^{m_2}{\Pred\,^3_i}'\subst{{\Post^2}'})\bigotimes_{i=0}^{m_1}\subst{{\Post^1_i}'}\\
+\Post'=(\bigotimes_{i=0}^{m_2}{\Post^3_i}')\subst{{\Post^2}'}\bigotimes_{i=0}^{m_1}\subst{{\Post^1_i}'}
+$\\
+\TODO{To check: ce n'est pas $m_1, m_2$ mais $m_1', m_2'$ such that 
+ $m_1'= m_1\setminus\Holes(Q)$???}\\
 
@@
 We proceed in the same way as for states named $u$.
-
-Therefore, we will obtain:
-
+To simplify the proof, we consider that in case 3, $Q$  moves, i.e, $\ostate{t_l^{l\in L_Q}} \neq \ostate{t_l'^{\,l\in L_Q}}$, else transition 3 of $Q$ should be skipped and the last $s_{p l}$ are equal to the first $u_{0 l}$.
+So we have: \\
 $\forall p \in [0\ldots n_1] Q\models{\openrule
 			{
-				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
-				{{\Post_p}\!\!''}}
+				(\beta^1_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred^1_p}''},  
+				{{\Post^1_p}''}}
 				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
@@
 				}%\]
-$
-and
+,$
 $ Q\models{\openrule
 			{
-				\beta_j^{j\in J\cap\Holes(Q)}, {\Pred}\,'',  
-				{\Post}\,''}
+				(\beta^2)_j^{j\in J\cap\Holes(Q)}, {\Pred^2}'',  
+				{\Post^2}''}
 			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'}
@@
 			{
-				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
-				{{\Post_p}\!\!''}}
+				(\beta^3_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred^3_p}''},  
+				{{\Post^3_p}''}}
 				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha'_{p}}
@@
 such that $n_1 \leq m_1$ and $n_2 \leq m_2$\\
-\TODO{We will discuss}
-
-For each  $\symb{OT}_p$ of $Q$ such that $p \in S$ and $S \subseteq [0\ldots (m_1\!+\!m_2)\!+\!1]$ in the form:
+By renaming all state names ($s$, $u$ and $t$) with the same state name $v$. We have:
+
+$\forall p \in [0\ldots (n_1+n_2+2)]\,\, Q\models{\openrule
+			{
+				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
+				{{\Post_p}\!\!''}}
+				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
+				\ostate{v_{(p+1)l}^{l\in L_Q}}}
+				}%\]
+$
+
+Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (are $\tau$ transition).
+By considering $\tau$  actions we split the sequence of actions into $n$ subsequences, such that each subsequence is a sequence of  $\tau$ action containing only one observable action.
+We can decompose each subsequence $k$ of length $len$  as follows:\\
+$\forall p \in [0\ldots (n'-1)] Q\models{\openrule
+			{
+				(\beta^1_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred^1_p}''},  
+				{{\Post^1_p}''}}
+				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
+				\ostate{v_{(p+1)l}^{l\in L_Q}}}
+				}%\]
+,$ 
+$Q\models{\openrule
+			{
+				(\beta^2)_j^{j\in J\cap\Holes(Q)}, {{\Pred^2}''},  
+				{{\Post^2}''}}
+				{\ostate{v_{n'l}^{l\in L_Q}} \OTarrow {\alpha_k}
+				\ostate{v_{(n'+1)l}^{l\in L_Q}}}
+				}%\]
+$
+and
+$\forall p \in [(n'+1)\ldots (len-1)]\,\, Q\models{\openrule
+			{
+				(\beta^3_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred^3_p}''},  
+				{{\Post^3_p}''}}
+				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
+				\ostate{v_{(p+1)l}^{l\in L_Q}}}
+				}%\]
+$\\ 
+\TODO{ Attention peut dire que ${{\Pred^1_p}''}, {{\Pred^2}''}$ are diffrent from previous one}\\ 
+Thereafter, by Lemma \ref{lem-rel-OT-WOT} we obtain the following weak open transition:
 \begin{mathpar}
@@
 			{
-				(\beta_p)_j^{J_p}, {\Pred_p},  
-				{\Post_p}}
-			{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
-				\ostate{s_{(p+1)l}^{l\in L_Q}}}
+			(\gamma_k)_j^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
+				{{\Post_k}}}
+			{\ostate{v_{l}^{l\in L_Q}} \OTWeakarrow {\alpha_{k}}
+				\ostate{v_{l}'^{l\in L_Q}}}
 		}%\]
-
-\end{mathpar}
-By rule (\WTTrois)  we can conclude that  we have:
-\begin{mathpar}
-Q\models{\openrule
-			{
-			(\gamma_p)_j^{J_p}, {\Pred_p}, {\Post_p}}
-			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha_{p}}
-				\ostate{s_{(p+1)l}^{l\in L_Q}}}
-		}%\]
-\end{mathpar}
-such that $\gamma_p = \vis{\beta_p}$.
-\TODO{maybe it is better to use $\gamma_p=[\beta_p]$}\\
-
-For  $\gamma_{j_0}=[\beta_0..\beta_n]$ we have $n$ open transitions  $\symb{OT}_p$ s.t $p\in [0\ldots n]$.
-
-Hence, we have forall $p\in [0\ldots n]$ :  
+\end{mathpar}
+$v_l=v_{0l} \wedge v_l'=v_{len}$\\
+$\forall j \in {j\in (J\cap\Holes(Q))},\quad
+\displaystyle{\gamma_{kj} }=\mybigdotcup_{i=0}^{(n'_1-1)}\!\!(\beta^1_{ij})\,\dotcup\,(\set{\beta^2})_j\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(len-1)}\!\!\!(\beta^3_{ij})
+\\
+\Pred_k=\!\!\bigwedge_{i=0}^{(n'_1-1)}\!\!
+{\Pred_i^1}''\land{\Pred^2}''\bigotimes_{i=0}^{(n'_1-1)}\subst{{\Post_i^1}''}\land \big(\!\!\!\!\!\bigwedge_{i=(n'+1)}^{(len-1)}\!\!{\Pred^3_i}''\subst{{\Post^2}''}\big)\bigotimes_{i=0}^{(n'_1-1)}\subst{{\Post^1_i}''}\\
+\Post_k=\big(\!\!\!\!\bigotimes_{i=(n'+1)}^{(len-1)}{\Post^3_i}''\big)\subst{{\Post^2}''}\bigotimes_{i=0}^{(n'_1-1)}\subst{{\Post^1_i}''}
+$\\
+
+In this case, the number of weak open transitions
+might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.\\
+For  $\gamma_{j_0}=[\beta_0..\beta_n]$ we have $n$ weak open transitions  $\symb{WOT}_p$ such that $p\in [0\ldots n]$.
+Therefore, we can conclude that we have forall $p\in [0\ldots n]$:  
 \begin{mathpar}
@@
 
+\TODO{I stopped there!}
 \end{proof}

### 2019-01-29 2016-Weak-FH-Bisim/WeakBisim.tex
skype notes

@@
 \TODO{Voir ou ajouter ceci: We introduce the notation ${\displaystyle \bigotimes_{i=1}^{n} \subst{Post_i}}$ to denote a combination of multiple substitution operations}
+
+${\displaystyle \bigotimes_{i=0}^{n} \subst{Post_i}} = \subst{Post_n}..\subst{Post_0}$
 \subsection{Weak bisimulation is an equivalence}
@@
          {
-           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
+           \set{\beta^3_i},\Pred\,^3_i,({x^3_{ik}\gets e^3_{ik}})^{k\in K_i}    }
          {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
@@
 \\
-\Pred=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2 \bigotimes_{i=0}^{n}\subst{\Post_i^1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\bigotimes_{i=0}^{n}\subst{\Post^1_i}\\
-\Post=({x^3_k\gets (e^3_k\subst {\Post^2})\subst{\Post^1_i}})^{k\in K}
+\Pred=\bigwedge_{i=0}^n(\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1})\land\Pred\,^2 \bigotimes_{j=0}^{n}\subst{\Post_j^1}\land (\bigwedge_{i=0}^m\Pred_i^3\bigotimes_{j=0}^{i-1}\subst{\Post_j^3}\subst{\Post^2}\bigotimes_{j=0}^{n}\subst{\Post^1_j})\\
+\Post={x^3_{mk}\gets (e^3_{mk}\bigotimes_{j=0}^{m-1}\subst{\Post_j^3}\subst{\Post^2}\bigotimes_{j=0}^{n}\subst{\Post^1_j})^{k\in K_m}}
 $
@@
 			{
-				(\beta^1_{p})_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
+				(\beta^1_{pj})^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
 				{\Pred^1_p}\!',  
@@
 			{
-				(\beta^1_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred^1_p}\!''},  
+				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred^1_p}\!''},  
 				{{\Post^1_p}\!''}}
@@
 $
-
+\TODO{from here simplify the double indices in beta and gamma}
 such that  $\Pred^1_p \iff {\Pred^1_p}\!'
@@
 where for all $l\in L$:\\
+\TODO{a reprendere avec la nouvelle decomp ; add the v of visible}
+
 $s_l=s_{0l} \wedge s_{{(m_1+1)}l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)}l=s'_l$\\
@@
 \Pred\,'=\bigwedge_{i=0}^{m_1}
-{\Pred_i^1}'\land{\Pred^2}'\bigotimes_{i=0}^{m_1}\subst{{\Post_i^1}'}\land (\bigwedge_{i=0}^{m_2}{\Pred\,^3_i}'\subst{{\Post^2}'})\bigotimes_{i=0}^{m_1}\subst{{\Post^1_i}'}\\
+({\Pred_i^1}'\bigotimes_{i=0}^{i-1}\subst{{\Post_i^1}'})
+\land{\Pred^2}'\bigotimes_{i=0}^{m_1}\subst{{\Post_i^1}'}\land (\bigwedge_{i=0}^{m_2}{\Pred\,^3_i}'(\bigotimes_{i=0}^{m_1}\subst{{\Post^1_i}'})\subst{{\Post^2}'}(\bigotimes_{j=0}^{i-1}\subst{{\Post^3_j}'}))\\
 \Post'=(\bigotimes_{i=0}^{m_2}{\Post^3_i}')\subst{{\Post^2}'}\bigotimes_{i=0}^{m_1}\subst{{\Post^1_i}'}
-$\\
-\TODO{To check: ce n'est pas $m_1, m_2$ mais $m_1', m_2'$ such that 
- $m_1'= m_1\setminus\Holes(Q)$???}\\
+$
 
@@
 Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (are $\tau$ transition).
-By considering $\tau$  actions we split the sequence of actions into $n$ subsequences, such that each subsequence is a sequence of  $\tau$ action containing only one observable action.
-We can decompose each subsequence $k$ of length $len$  as follows:\\
+By considering $\tau$  actions we split the sequence of actions into $n$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.
+We can decompose each of the $n$ subsequences, where sequence  $k$ has length $n_k$,  as follows:\\
 $\forall p \in [0\ldots (n'-1)] Q\models{\openrule
@@
 and
-$\forall p \in [(n'+1)\ldots (len-1)]\,\, Q\models{\openrule
+$\forall p \in [(n'+1)\ldots (n_k-1)]\,\, Q\models{\openrule
 			{
@@
 \end{mathpar}
-$v_l=v_{0l} \wedge v_l'=v_{len}$\\
+$\forall l. v_l=v_{0l} \wedge v_l'=v_{n_kl}$\\
 $\forall j \in {j\in (J\cap\Holes(Q))},\quad
@@
 might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.\\
-For  $\gamma_{j_0}=[\beta_0..\beta_n]$ we have $n$ weak open transitions  $\symb{WOT}_p$ such that $p\in [0\ldots n]$.
-Therefore, we can conclude that we have forall $p\in [0\ldots n]$:  
+
+\TODO{link gamma j 0 with the alpha k ; this ises the visible abstraction and the ewautaions of 1,2,3 decomposition}
+For  $\gamma_{j_0}=[\beta_0..\beta_n]$ we have $n$ weak open transitions  $\symb{WOT}_k$ such that $k\in [0\ldots n]$.
+Therefore, we can conclude that we have for all $k\in [0\ldots n]$:  
 \begin{mathpar}
@@
 			{
-			(\gamma_p)_j^{J_p}, {\Pred_p}, {\Post_p}}
-			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha_{p}}
+			\gamma_{kj}^{j\in J_k}, {\Pred_k}, {\Post_k}}
+			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha_{k}}
 				\ostate{s_{(p+1)l}^{l\in L_Q}}}

### 2019-01-29 2018-Arch-pNets/arch-pNets.tex

--- 2019-01-28 2018-Arch-pNets/arch-pNets.tex
@@
 
+\label{property:reset}
 \addSB{Although we define properties as state predicates, any
@@
 \begin{example}[An open-transition]
-  \label{OT:enable-composed}
+  \label{Example:TimerOT3}
   The \texttt{Failure TimerMonitor} pNet of \Fig{FailureTimer:pNet} has \replaceSB{2 controllers 
@@
   \label{fig:FailureTimer:pNet}
-%
-  \noteSBin{The updated encoding exports more primed variables in the
-    actions, \eg $tick(z,t,z',t')$ and $fail(zone, zone', b1)$ instead
-    of $tick(z,t,z')$ and $fail(zone, b1)$, and SVs, \eg $\dots \land
-    (t' = t) \land (zone' = zone)$ in the guard of SV0. Shall we
-    update the figure to include these or, rather, explain that the
-    figure is cleaned-out for readability?}
+%% %
+%%   \noteSBin{The updated encoding exports more primed variables in the
+%%     actions, \eg $tick(z,t,z',t')$ and $fail(zone, zone', b1)$ instead
+%%     of $tick(z,t,z')$ and $fail(zone, b1)$, and SVs, \eg $\dots \land
+%%     (t' = t) \land (zone' = zone)$ in the guard of SV0. Shall we
+%%     update the figure to include these or, rather, explain that the
+%%     figure is cleaned-out for readability?}
 %
@@
   \caption{The open Automaton of the Failure Monitor Architecture}
-  \label{schema:ArchFailure:BIP}
+  \label{schema:ArchFailure:OA}
 \end{figure}
@@
 detail of the open transition, but only the assignement of state
-variables, and the resulting action. You can find the full details in
-Appendix \ref{secn:full-results}. As an example, $OT_3$ is the one explained in Example
-\ref{Example:TimerOT3} page \pageref{Example:TimerOT3}
-
-\todoEM{12 open transitions... Comments on the predicates ???}
+variables, and the resulting action; you can find the full details in
+Appendix \ref{secn:full-results}. As an example, $OT_3$ is the one
+explained in Example~\ref{Example:TimerOT3} page~\pageref{Example:TimerOT3}
+
+This automaton has 12 transitions, including those encoding various
+possible firing of some interactions (e.g. OT 2 and 3 for
+$fail$). At first sight, it appears the rough behaviour is
+reasonable, although a detailed study shows that the property stated
+in page~\pageref{property:reset} does not hold, because of the
+$fail$ loops on states $11$ and $12$. This is because we did not use
+the maximal progress assumption here. If we do, we get the corrected
+behaviour in Fig~\ref{schema:ArchFailure:MaxProgress}. This one
+verifies all the properties listed in  \app{properties}.
 

### 2019-01-31 2018-Arch-pNets/arch-pNets.tex
switch pnet and archi
Imported biblio from net paper
Notations in 1 page, we can remove more I believe

@@
 
-\section{Previous results: Architecture and pNets}
-
-\subsection{Preliminaries}
+\section{General Notations and pNets previous results} 
 \label{secn:preliminaries}
@@
 
-\subsubsection{Notations}
+\subsection{Notations}
 \label{secn:notations}
@@
 E.g., $a^{i\in\{3\}}$ is the mapping with a single entry $a$ at index
-$3$ ; abbreviated $(3\mapsto a)$ in the following.
+$3$ ; also abbreviated $(3\mapsto a)$.
 When this is not
@@
 write $x\in a_i^{i\in I}$ to mean $\exists i\in I.\, x=a_i$.  An empty
-family is denoted $\emptyset$. We use a classical overline notation, \eg $\overline{a}$, 
-for a family, where the indexing set is irrelevant. Finally, we use $\uplus$ to denote 
-the disjoint union on
-indexed sets.
-
-\noteIn{states looks ok, but initial state is $s_0$ in pNet and not in archi : $s^0$.  Exponent 
-position was removed from pNet because we found it complex with indexed set notation but 
-could be ok.
-\Ludo
-
-I am using exponent notation for ``modifiers'', reserving\mdash
-as much as possible\mdash index notation for enumeration.  I
-think this can be solved, where necessary, by using parentheses,
-\eg $(s^0_i)^{i \in I}$
-\Simon
-}
+family is denoted $\emptyset$.
+
+%\noteIn{states looks ok, but initial state is $s_0$ in pNet and not in archi : $s^0$.  Exponent 
+%position was removed from pNet because we found it complex with indexed set notation but 
+%could be ok.
+%\Ludo
+%
+%I am using exponent notation for ``modifiers'', reserving\mdash
+%as much as possible\mdash index notation for enumeration.  I
+%think this can be solved, where necessary, by using parentheses,
+%\eg $(s^0_i)^{i \in I}$
+%\Simon
+%}
 
 %****************************************************************
-
-\subsubsection{Term algebra}
-\label{secn:terms}
-
-\todoLHin{Remove term algebra or simplify?}
-\todoLHin{universal domain $\implies$ remove sort}
-\todoLHin{replace assignments by $e_i$
-
-  In fact, in the pNet action terms, you need expressions, not
-  assignements.  Therefore assuming that all expressions are
-  assignments will not work, so the right approach is to have
-  expressions (for pNets) and assignments (for BIP) separately.
-  \Simon
-%
-}
-
-\noteSBin{In Archi we have $a$, whereas in pNets we have $\alpha$, where, approximately $\alpha = 
-a(x_1..x_n)$, except that $a$ is port name in archi and action name in pNets.
-Is this true? can we unify better? or is it sufficient?
-\Ludo
-
-$a$ is a set of ports, but otherwise, yes, this is true.  I think
-this is coherent, since, in archi, we have the ``interaction
-part'', \ie only ports, plus the data part, \ie variables,
-guards, expressions.  In pNets, these are combined.  So, it seems
-ok that notations differ\mdash ``uniformisation'' will be
-achieved by encoding archi $\rightarrow$ pNets.
-}
-
-\noteLHin{I believe we should simplify this paragraph about param actions
-
-  I agree with this, but also we may look at what is useful here, and what is only used later in pLTS/pNet definitions. 
-\Eric}
-The pNet model in \secn{pNets} relies on a notion of parameterised actions, that are
-symbolic expressions using data types and variables. As we aim at encoding the low-level 
-behaviour of possibly very different
-programming languages, we do not want to impose one specific algebra
-for denoting actions, nor any specific communication mechanism. So we
-leave unspecified the constructors of the algebra that will allow building
-expressions and actions. Moreover, we use a generic {\em action interaction}
-mechanism, based on (some sort of) unification between two or more action
-expressions, to express various kinds of communication or
-synchronisation mechanisms.
-
-%\def\Talg{\mathcal{T}_{\Sigma,\P}}  % Moved to the header
-
-\noteSBin{proposed notations:
-
-  $g$ are boolean expressions;
-  $e_i$ are updates/assignments
-  \Ludo
-
-  In fact, I am not sure whether I have correctly understood this
-  suggestion: do you mean, \eg using $g$ to denote the set of
-  Boolean expressions or individual Boolean expressions? Using
-  lower case letters to denote sets might be problematic, since
-  we (at least I) use them a lot to denote instances, as in
-  \[q \goesto{a, g, e} q'\,.\]
-  %% In fact, I even use capital letters: in the definition of
-  %% interaction model composition, I use
-  %% \[\cdot \goesto{a, G, E} \cdot\]
-  %% in the conclusion of the rule.  However, for this latter I can
-  %% easily change the notation.
-
-  I have set up macros for, general and Boolean expressions,
-  actions, variables \etc[,] which I have substituted everywhere,
-  where appropriate in the following paragraph.
-}
-
-  \begin{tabular}{
-      @{}p{0.15\columnwidth}@{}
-      p{0.35\columnwidth}@{}
-      p{0.5\columnwidth}@{}
-    }
-    {\bf Output} & {\bf Command} & {\bf Definition}
-    \\
-    $\data$ &
-    {\ttfamily\textbackslash data} &
-    {\ttfamily\textbackslash sD}
-    \\
-    \signature &
-    {\ttfamily\textbackslash signature} &
-    {\ttfamily\textbackslash Sigma}
-    \\
-    \variables &
-    {\ttfamily\textbackslash variables} &
-    {\ttfamily\textbackslash cV}
-    \\
-    \Talg &
-    {\ttfamily\textbackslash Talg} &
-    {\ttfamily\textbackslash cT\_\{\textbackslash signature,\textbackslash variables\}}
-    \\
-    \actions{\#1} &
-    {\ttfamily\textbackslash actions\{\#1\}} &
-    {\ttfamily\textbackslash cA\_\{\#1\}}
-    \\
-    \exprs{\#1} &       
-    {\ttfamily\textbackslash exprs\{\#1\}} &
-    {\ttfamily\textbackslash sE\_\{\#1\}}
-    \\
-    \monexprs{\#1} &       
-    {\ttfamily\textbackslash monexprs\{\#1\}} &
-    {\ttfamily\textbackslash sE\^{}\{<\}\_\{\#1\}}
-    \\
-    \boolexprs{\#1} &       
-    {\ttfamily\textbackslash boolexprs\{\#1\}} &
-    {\ttfamily\textbackslash sB\_\{\#1\}}
-    \\
-    \guards{\#1} &
-    {\ttfamily\textbackslash guards\{\#1\}} &
-    {\ttfamily\textbackslash sB\^{}\{<\}\_\{\#1\}}
-    \\
-    \assigns{\#1} &
-    {\ttfamily\textbackslash assigns\{\#1\}} &
-    {\ttfamily\textbackslash sA\_\{\#1\}}
-    \\
-    \updates{\#1} &
-    {\ttfamily\textbackslash updates\{\#1\}} &
-    {\ttfamily\textbackslash sA\^{}\{<\}\_\{\#1\}}
-    \\
-    \valuations{\#1} &
-    {\ttfamily\textbackslash valuations\{\#1\}} &
-    {\ttfamily\textbackslash data\^{}\{\#1\}}
-    \\[6pt]
-    \val[]{\#2}{\#3} &
-    {\ttfamily\textbackslash val[]\{\#2\}\{\#3\}} &
-    {\ttfamily\#1\{\textbackslash sigma\}\^{}\{\#2\}\_\{\#3\}}
-    \\[6pt]
-    \val[\tilde]{\#2}{\#3} &
-    {\ttfamily\textbackslash val[\textbackslash tilde]\{\#2\}\{\#3\}} &
-    (optional argument usage examples)
-    \\[6pt]
-    \val[\primeit]{\#2}{\#3} &
-    {\ttfamily\textbackslash val[\textbackslash primeit]\{\#2\}\{\#3\}} &
-    \\[6pt]
-    \val[\secondit]{\#2}{\#3} &
-    {\ttfamily\textbackslash val[\textbackslash secondit]\{\#2\}\{\#3\}} &
-  \end{tabular}
-\noteSBin{commands above (tabular generates an error inside a
-  note)}
-
-Formally, we assume the existence of a term algebra $\Talg$,
+We assume the existence of a term algebra $\Talg$,
 where $\signature$ is the signature of the data and action constructors,
 and $\variables$ a set of \emph{variables}. Within $\Talg$, we distinguish a set of
-\emph{data expressions} $\exprs{\variables}$ and a set of \emph{Boolean
-expressions} \todoLH{$\mathcal{B} \to g$}
-$\boolexprs{\variables}\subseteq\exprs{\variables}$.
+\emph{data expressions} $\exprs{\variables}$; $e_i$ ranges over boolean expressions, and a set of \emph{Boolean
+expressions} 
+$\boolexprs{\variables}\subseteq\exprs{\variables}$, $g$ (guards) ranges over boolean expressions.
 On top of $\exprs{\variables}$ we build the \emph{action algebra}
-$\actions{\variables}$, with $\actions{\variables}\subseteq\Talg$ \replaceSB{,}{and}
-$\exprs{\variables}\cap\actions{\variables} = \emptyset$;
-naturally action terms will use data expressions as subterms.
-\addSB{In addition to the above notations, we will use
+$\actions{\variables}$, with $\actions{\variables}\subseteq\Talg$.
+We  use
 \[
@@
 \]
-to denote the set of \emph{variable assignments}.}  We use the symbol
-$\noop$ to denote the empty assignment, \ie an assignment with
-$I = \emptyset$.
-
-To be able to reason about the data flow between pLTSs, we
+to denote the set of \emph{variable assignments}.  $u$ ranges over sets of assignments.
+To be able to reason about the data flow between actions, we
 distinguish \emph{input variables} of the form $?x$ within terms; the function
@@
 $t\in\Talg$, and $iv(t)$ returns its input variables.
-Action algebras can naturally encode usual point-to-point message passing calculi (using 
-$a(?x_1,\dots,?x_n)$ for inputs, $a(v_1,\dots,v_n)$ for outputs), but it also allows
-for more general mechanisms, like gate negotiation in Lotos, or broadcast
-communications.
-
-Finally, we assume the existence of a universal data domain
+
+We assume the existence of a universal data domain
 given as a partially-ordered set $(\data, \order)$, potentially
 encompassing several copies of any given data type with
-different orders.  For example, we assume that $(\data,
+different orders.  We assume that $(\data,
 \order)$ comprises both the unordered set of Booleans $\sB =
@@
 intervals ordered by inclusion.
-%
-\addSB{In practice, and in the examples of
-this paper, all the variables are sorted, meaning that their values
-can only range over given subsets of $\data$, such as $\sB$ or
-$\sB^<$.
+%In practice, and in the examples of
+%this paper, all the variables are sorted, meaning that their values
+%can only range over given subsets of $\data$, such as $\sB$ or
+%$\sB^<$.
 %
 When speaking of an ordered sort, \eg $\sB^<$, we will assume that it
-forms a meet-semilattice and denote by $\wedge$ the corresponding meet
-operator.}
+forms a meet-semilattice and denote by $\wedge$ the meet
+operator.
 
@@
 the set of \emph{valuations} of the variables in $V$.
-Valuations extend canonically to expressions.  Thus
-$\val{}{}(x)$ and $\val{}{}(e)$ denote, respectively, the
-values of the variable $x$ and the expression $e$ under the
-valuation $\val{}{}$.
-%
+Valuations extend canonically to expressions and denote $\val{}{}(e)$ the value of $e$ under the valuation $\val{}{}$.
+\noteLH{its the following really necessary}
 \addSB{Since we consider variables to be sorted, valuations
@@
   $\exprs{V} \rightharpoonup \data$.}
-
-For a valuation $\val{}{} \in
-\valuations{V}$ and an assignment $(x_i := e_i)^{i \in I} \in
-\assigns{V}$, we denote $\val{}{}[(x_i := e_i)^{i \in I}]$ the
-valuation defined by
+For a valuation $\val{}{}$ and an assignment $(x_i := e_i)^{i \in I}$, we define:
 \[
@@
 iff $\val{1}{}(x) \order \val{2}{}(x)$, for all $x \in V$.  An
-expression $e \in \exprs{V}$ is called \emph{monotonic} if, for
-any two valuations $\val{1}{}, \val{2}{} \in \valuations{V}$,
+expression $e$ is  \emph{monotonic} if, for
+any two valuations $\val{1}{}, \val{2}{}$,
 $\val{1}{} \order \val{2}{}$ implies $\val{1}{}(e) \order
@@
 %
-Similarly, an assignment $(x_i := e_i)^{i \in I} \in \assigns{V}$ is
-called monotonic if all expressions $e_i^{i \in I}$ are monotonic.
-We will denote $\guards{V} \subset \boolexprs{V}$, $\monexprs{V}
+Similarly, an assignment $(x_i := e_i)^{i \in I} $ is
+ monotonic if all expressions $e_i^{i \in I}$ are monotonic.
+We  denote $\guards{V} \subset \boolexprs{V}$, $\monexprs{V}
 \subset \exprs{V}$ and $\updates{V} \subset \assigns{V}$ the sets of
@@
 %
-
-%****************************************************************
-%****************************************************************
-
-\subsection{The theory of architectures with data}
-\label{secn:archs}
-
-%****************************************************************
-
-\subsubsection{Components and composition}
-\label{secn:components}
-
-%% \noteSBin{%
-%% To guarantee preservation of properties guards and expressions
-%% have to be \emph{monotonic}.  In the case of a trivial order, \ie
-%% when nothing is comparable, \emph{any guard or expression is
-%%   monotonic}.  Thus, this is not really a constraint!
-
-%% Do we put this in the definition of expressions and guards or in
-%% the definitions of components and interaction models?
-%% }
-
-\begin{definition}[Components]
-  \label{defn:component}
-  A \emph{component} is a tuple $\tuple{Q, q^0, V, \val{0}{}, P,
-  \export, \goesto{}}$, where
-  \begin{itemize}
-  \item $Q$ is a set of \emph{states}, with $q^0 \in Q$ the
-    \emph{initial state}, 
-  \item $V$ is a set of \emph{component variables},
-  \item $\val{0}{} : V \rightarrow \data$ is an \emph{initial
-    valuation} of the component variables, 
-  \item $P$ is a set of \emph{ports}, with
-    $\export : P \rightarrow 2^V$ 
-    the \emph{set of variables exported by each port},
-  \item $\goesto{}\, \subseteq
-    Q \times (2^P\setminus \{\emptyset\}) \times \guards{V} \times \updates{V} \times Q$
-%
-    is a \emph{transition relation}, with transitions
-    labelled by \emph{interactions}, \ie triples consisting of a non-empty set of ports,
-    %% $\emptyset \neq a \subseteq P$,
-    a monotonic Boolean \emph{guard}
-    %% $g \in \guards{V}$ 
-    and a monotonic \emph{update assignment}.
-    %% \hl{$u \in \updates{V}$}.
-  \end{itemize}
-%
-  We call the triple $(V,P, \export)$ the \emph{interface} of the
-  component.\,\footnote{%
-%
-  In practice, only exported variables, \ie those in the set
-  $\bigcup_{p \in P}\export(p)$, belong to the component interface and
-  can be used for the interactions with other components (see
-  \defn{im}).  However, in the context of this paper we can simplify
-  by omitting this separation.
-%
-  }
-%
-  Notations $q \goesto{a, g, u} q'$ and $q \goesto{a, g, u}$ are as usual;
-  for a component $B$, we denote $Q_B$, $q^0_B$, $V_B$, $\val{0}{B}$, $P_B$,
-  and $\export[B]$ the corresponding constituents of $B$.  We will
-  skip the index on the transition relations $\goesto{}$, since it
-  is always clear from the context.
-\end{definition}
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=0.9\columnwidth]{BIPspec-ArchFailureTimerMax-v4}
-  \caption{The BIP specification of the Failure Monitor architecture}
-  \label{fig:schema:ArchFailure:BIP}
-\end{figure}
-
-In this paper, we will use a running example, which is a refined
-version of the Failure Monitor architecture
-from~\cite{CubETH-case-study}.  Although \fig{schema:ArchFailure:BIP}
-shows the full definition of this architecture, we will explain its
-various elements progressively, as we define the corresponding
-notions.
-
-The model in \fig{schema:ArchFailure:BIP} has  components
-%% The
-%% component $\NameOprnd$ is an \emph{operand} of the architecture, \ie
-%% it only has its interface defined: $(\emptyset, \{\PortFinish,
-%% \PortResume, \PortFail\}, \export[\emptyset])$, with
-%% $\export[\emptyset](p) = \emptyset$, for all $p \in \{\PortFinish,
-%% \PortResume, \PortFail\}$.  
-%% The other two components,
-%
-$\NameTimer$(imer) and $\NameCtrl$(ontrol), with interfaces
-$\btuple{
-  \{t, z\},
-  \{\PortTick, \PortCancel, \PortTOT\},
-  \bigl\{\PortTick \mapsto \{t, z\}\bigr\}
-}$,
-and
-$\btuple{
-  \{\mathit{zone}\},
-  \{\PortReset, \PortFail, \PortResume, \PortTOC\},
-  \bigl\{\PortFail \mapsto \{\mathit{zone}\}\bigr\}
-}$, respectively.
-%
-%% \[
-%% \begin{array}{@{}c@{\hspace{3mm}}c@{}}
-%%   \bigl(
-%%   \{t, z\},
-%%   \{\PortTick, \PortCancel, \PortTOT\},
-%%   \export[\NameTimer]
-%%   \bigr)\,,
-%%   %% \qquad
-%%   &
-%%   \bigl(
-%%   \{\mathit{zone}\},
-%%   \{\PortReset, \PortFail, \PortResume, \PortTOC\},
-%%   \export[\NameCtrl]
-%%   \bigr)\,,
-%%   \\
-%%   \export[\NameTimer](p) =
-%%   \begin{cases}
-%%     \{t, z\}, & \text{if } p = \PortTick,\\
-%%     \emptyset, & \text{otherwise,}
-%%   \end{cases}
-%%   %% \]
-%%   %% and
-%%   %% \[
-%%   %% \quad
-%%   &
-%%   \export[\NameCtrl](p) =
-%%   \begin{cases}
-%%     \{\mathit{zone}\}, & \text{if } p = \PortFail,\\
-%%     \emptyset, & \text{otherwise.}
-%%   \end{cases}
-%% \end{array}
-%% \]
-%
-%% , where $\export[\NameCtrl](\PortFail) =
-%% \{\mathit{zone}\}$ and $\export[\NameCtrl](p) = \emptyset$, for all
-%% other ports $p$; $\export[\NameTimer](\PortTick) = \{t, z\}$ and
-%% $\export[\NameTimer](p) = \emptyset$, for all other ports $p$.
-Variable $t$ is implicitly assumed to be an integer.  Variables $z$
-and $\mathit{zone}$ are implicitly assumed to be integer intervals of
-the form $[l,u]$.  For both types, we also implicitly assume the
-natural ordering: increasing integers and interval inclusion.
-
-%% are \emph{coordinators}\mdash they are specified
-%% completely, including the states and transitions defining their
-%% \emph{behaviour}.
-Component \emph{behaviour} is defined by states %% ($\{\cstate{0},
-%% \cstate{1}, \cstate{2}\}$, for $\NameCtrl$; $\{\tstate{0}\}$, for
-%% $\NameTimer$)
-and transitions.
-The initial states
-\tstate{0} and \cstate{0}, and valuations $\val{0}{\NameTimer} = \{t
-\mapsto 0, z \mapsto \topinterval\}$ and $\val{0}{\NameCtrl} =
-\{\mathit{zone} \mapsto [\mathrm{Min}, \mathrm{Max}]\}$ are shown by
-the incoming arrows $\goesto{\TimerInit[]} \tstate{0}$ and
-$\goesto{\IntervalInit[]} \cstate{0}$.\footnote{%
-%
-  We use $\topinterval$ to denote the top interval in the inclusion
-  order, \ie $(-\infty, +\infty)$.
-%
-} The constants $\mathrm{Min}$ and $\mathrm{Max}$ are the parameters
-of the architecture.
-
-Transitions are labelled with ports of the
-corresponding components, Boolean guards and update assignments on local
-variables.  \Eg[,] the loop transition $\tstate{0}
-\goesto{\PortTick, \GuardTick[], \TimerUpd[]} \tstate{0}$ in the
-component $\NameTimer$ is labeled by the port $\PortTick$.  It can be
-fired only when the current value of the local variable $t$ is less
-than $z.u$.
-%% , where $z = [l, u]$ is a local variable representing an
-%% interval
-Upon firing, this transition increments the value of $t$ by $1$.  The
-guards and update assignments of the transitions of $\NameCtrl$ are
-omitted.  The default values are the constant predicate $\true$ (true) and
-the empty assignment {\noop}, respectively.  
-%\noteLH{It looks like Max is in zone, I do not understand}
-%
-Clearly, all guards and update assignments are monotonic.
-
-%% \todoSBin{Speak of guard monotonicity}
-
-\begin{definition}[Component semantics]
-  \label{defn:comp:semantics}
-  The \emph{semantics} of a component $B = \tuple{Q, q^0, V,
-  \val{0}{}, P, \export, \goesto{}}$ is %% given by
-  the LTS denoted $\semopen{B} = \tuple{S,
-  s^0, \goesto{}}$, where $S = Q \times \valuations{V}$, $s^0 =
-  \tuple{q^0, \val{0}{}}$ and $\goesto{}$ is the minimal transition
-  relation satisfying the rule
-  %
-  \begin{equation}
-    \label{eq:comp:semantics}
-    \infer{
-      q \goesto{a, g, u} q'
-      \and
-      \val{}{} \models g
-      \and
-      \val[\primeit]{}{} = \tilde{\val{}{}}[u]
-      \and
-      \valdiff{\val{}{}}{\tilde{\val{}{}}} \subseteq \export(a)
-    }{
-      (q, \val{}{}) \goesto{a,\tilde{\val{}{}}} (q', \val[\primeit]{}{})
-    }
-    \,.
-  \end{equation}
-  %
-  %% \todoSB{Do we actually need this?}\todoLH{I agree: I do not think we need this}
-  %% \hl{The \emph{closed semantics} of $B$ is given by the LTS denoted
-  %% $\semclosed{B} \bydef{=}\reachable{\semopen{B}}$, comprising
-  %% only the reachable states of $\semopen{B}$.}
-\end{definition}
-
-The use of the intermediate valuation $\tilde{\val{}{}}$ in the
-conclusion and the third premise of rule \eq{comp:semantics}
-allows some of the variables to get new values before the
-transition is actually fired.  Thus the component is \emph{open}
-to the exchange of data with its environment.  However, the
-fourth premise in \eq{comp:semantics} restricts the set of
-variables, which can be affected by such data transfer, to those
-that are exported through the ports participating in the
-interaction.
-
-\begin{definition}[Interaction model]
-  \label{defn:im}
-  For a finite set of component interfaces $(V_i, P_i,
-  \export[i])^{i \in I}$, such that all $P_i$ and all $V_i$ are
-  pairwise disjoint, %% \ie $\forall i \neq j,\ P_i \cap P_j = V_i \cap
-  %% V_j = \emptyset$. 
-  let $P = \bigcup_{i \in I} P_i$, $V = \bigcup_{i
-    \in I} V_i$ and $\export : P \rightarrow 2^V$ such that, for any
-  $p \in P_i$, $\export(p) = \export[i](p)$. 
-%
-  %% \noteSB{Updated this}\hl{and $V_a \bydef{=} \bigcup_{i \in
-  %%   \supp{a}} \export[i](a \cap P_i)$ the set of component
-  %% variables exported through $a$.}
-
-  An \emph{interaction model over $(V, P, \export)$} is a set $\Gamma
-  \subseteq 2^P \times \guards{V} \times \updates{V}$, such that,
-  for any interaction $(a, g, u) \in \Gamma$, we have
-  $g \in \guards{\export(a)}$ and $e \in \updates{\export(a)}$.\footnote{%
-%
-    Notice that this definition allows $(\emptyset, \true,
-    \noop)$ and $(\emptyset, \false, \noop)$ to be included in
-    $\Gamma$.
-%
-  }
-  %% We call the set of ports $P$ the \emph{domain} of the
-  %% interaction model.
-\end{definition}
-
-%% \noteLH{supp should go outside the definition}
-When speaking of a set of components or interfaces, we will always
-assume that it satisfies the disjointness assumption of \defn{im}.
-%
-We call the \emph{support} of a set of ports $a \subseteq P$, denoted
-$\supp{a}$, either the set $\setdef{i \in I}{a \cap P_i \neq
-  \emptyset}$ (for $P = \bigcup_{i=1}^n P_i$) or the set $\setdef{B
-  \in \cB}{a \cap P_B \neq \emptyset}$ (for $P = \bigcup_{B \in \cB}
-P_B$).  The precise meaning of this notation will always be clear from
-the context.  Intuitively, for an interaction $(a, g, u)$, $\supp{a}$
-denotes the set of the participating components.
-
-\begin{definition}[Composition]
-  \label{defn:im:sem}
-  The \emph{composition} of a finite set of components $\cB = \tuple{Q_i,
-  q^0_i, V_i, \val{0}{i}, P_i, \export[i], \goesto{}}^{i \in I}$ with
-  the interaction model $\Gamma$ over $\tuple{V, P, \export}$ (as in \defn{im})
-  is the component $\Gamma(\cB) = \tuple{Q, q^0, V, \val{0}{}, P,
-    \export, \goesto{}}$, where
-%
-  $Q = \prod_{i \in I} Q_i$;
-%
-  $q^0 = (q_i^0)^{i \in I}$;
-%
-  $\val{0}{}: V \rightarrow \data$ is such that, for any $v \in
-  V_i$, $\val{0}{}(v) = \val{0}{i}(v)$;
-%
-  and $\goesto{}$ is the minimal transition relation satisfying
-  the rule
-%
-  \begin{gather*}
-%%     \label{eq:im:empty}
-%%     \infer{
-%%       q_j \goesto{\emptyset, g, e} q_j'
-%%       \and
-%%       \forall i \neq j, q_i = q_i'
-%%     }{
-%%       (q_i)^{i \in I} \goesto{\emptyset, g, e} (q_i')^{i \in I}
-%%     }\,,
-%% %
-%%     \\[0.5\baselineskip]
-    \label{eq:im:sem}
-%
-    \infer{    
-      (a, g, u) \in \Gamma
-      \and
-      a \neq \emptyset
-      \and
-      \forall i \in \supp{a}, q_i \goesto{a \cap P_i, g_i, u_i} q_i'
-      \and
-      \forall i \not\in \supp{a}, q_i = q_i'
-%
-      \\\\
-      \textstyle
-%
-      g' = g \land \bigwedge_{i \in \supp{a}} g_i
-      \and
-      u' = u; u_i^{i \in \supp{a}}
-    }{
-      (q_i)^{i \in I} \goesto{a, g', u'} (q_i')^{i \in I}
-    }\,.
-  \end{gather*}
-  %% \todoSBin{Add the intuitive explanation}
-\end{definition}
-
-\addSB{Intuitively, an interaction can be fired if all the involved
-  components are ready to fire their corresponding transitions.  The
-  other components do not change their states.  Both the interaction
-  guard and those of the participating transitions must be satisfied.
-  The update assignment of the interaction is executed first, followed
-  by those of the components.}
-
-Specifying interaction models as sets of sets of ports is not
-practical due to their potentially exponential size.  An algebra of
-connectors was introduced in \cite{BliSif08-acp-tc} in order to
-structure interactions in BIP models.
-
-Connectors are hierarchical, tree-like structures with component ports
-at the leaves.  They define sets of interactions, based on the
-attributes of the nodes, which may be either \emph{trigger}
-(triangles in \fig{schema:ArchFailure:BIP}) or \emph{synchron}
-(bullets in \fig{schema:ArchFailure:BIP}).
-%
-If all sub-connectors of a connector are synchrons, then an
-interaction is allowed by the connector only if each subconnector
-can contribute.
-%
-If at least one of the sub-connectors is a trigger, then any
-interaction consisting of contributions of any set of sub-connectors
-\emph{involving at least one of the triggers} is allowed.
-%
-The interaction model is defined as the set of all interactions
-allowed by at least one of the connectors in the system.
-%% The composition semantics of BIP systems consists in
-%% firing exactly one interaction, enabled through at least one of the
-%% top-level connectors, at each execution round.
-
-For instance, the connector {\NameTimer.\PortTick
-  \trigsynch (\PortFail \trigsynch \NameCtrl.\PortFail)} is a
-two-level hierarchical connector.  In the second-level subconnector
-{\PortFail \trigsynch \NameCtrl.\PortFail}, the port {\PortFail} is a
-trigger, whereas {\NameCtrl.\PortFail} is a synchron.  Therefore, this
-subconnector allows two interactions labelled $\{\PortFail\}$ and $\listset{\NameCtrl.\PortFail, \PortFail}$.  Similarly, at the top level,
-{\NameTimer.\PortTick} is a trigger, whereas the second-level
-subconnector is a synchron.  Hence, the overall connector allows the
-interaction involving only one port {\NameTimer.\PortTick}\footnote{%
-%
-  Such interactions are called \emph{singleton interactions}.
-%
-} and any interaction involving both {\NameTimer.\PortTick} and
-\emph{some} interaction of the second-level subconnector.  Combining
-the two levels we can see that the entire connector defines the
-following three interactions (observe that $\topinterval +
-\NameTimer.t = \topinterval$ and $\NameTimer.z \cap \topinterval =
-\NameTimer.z$):
-%
-\begin{gather*}
-  \bigl(\{\NameTimer.\PortTick\},
-  \true, \emptyset\bigr)
-  %% \NameTimer.z := \NameTimer.z\bigr)
-  ,
-%
-  \qquad
-%
-  \bigl(\{\PortFail, \NameTimer.\PortTick\},
-  \true, \emptyset\bigr)
-  %% \NameTimer.z := \NameTimer.z\bigr)
-  ,
-%
-  \\
-%
-  \bigl(\{\NameCtrl.\PortFail, \PortFail, \NameTimer.\PortTick \},
-  \true,
-  \NameTimer.z := \NameTimer.z \cap (\NameCtrl.\mathit{zone} + \NameTimer.t)\bigr)
-  .
-\end{gather*}
-%% \begin{align*}
-%%   \bigl(\{\NameTimer.\PortTick\}&,
-%%   \true, 
-%%   \NameTimer.z := \NameTimer.z\bigr)
-%%   \,,\\
-%%   \bigl(\{\PortFail, \NameTimer.\PortTick\}&,
-%%   \true,
-%%   \NameTimer.z := \NameTimer.z\bigr)
-%%   \,,\\
-%%   \bigl(\{\NameCtrl.\PortFail, \PortFail, \NameTimer.\PortTick \}&,
-%%   \true,
-%%   \NameTimer.z := \NameTimer.z \cap (\NameCtrl.\mathit{zone} + \NameTimer.t)\bigr)
-%%   \,.
-%% \end{align*}
-
-%% \todoSB{Update this}
-%% \hl{For instance, in \fig{schema:ArchFailure:BIP}, the two ports
-%% $\NameTimer.\PortStart$ and $\NameCtrl.\PortFail$ are always
-%% synchronised, since they belong to exactly one binary sub-connector,
-%% where they are both synchrons.  In particular, this means that
-%% whenever the transition \cstate{0} \goesto{\PortFail} \cstate{1} is
-%% fired, so is the transition \tstate{0} \goesto{\PortStart,
-%%   \TimerInit[]} \tstate{1}, initialising the timer.  The binary
-%% connector $\NameTimer.\PortStart \twosynch
-%% \NameCtrl.\PortFail$ is a sub-connector of a hierarchical connector,
-%% where the port $\NameOprnd.\PortFail$ is a trigger.  Thus, the above
-%% interaction can only happen together with $\NameOprnd.\PortFail$,
-%% forming a ternary interaction.  On the contrary, being a trigger, the
-%% port $\NameOprnd.\PortFail$ can fire alone, forming a singleton
-%% interaction.}
-
-%% \todoSBin{Speak of data transfer}
-
-%% \todoSBin{Provide the interaction model}
-
-\begin{definition}[Priority model]
-  \label{defn:priority}
-  A \emph{priority model} over a component interface $(V, P,
-  \export)$\footnote{%
-%
-    Notice that the export function $\export$ has no impact on the
-    priority model definition.
-%
-  } is a strict partial order on interactions: $\pi
-  \subseteq \bigl(2^P \times \guards{V} \times \updates{V} \bigr)^2$.
-
-  We write $\alpha \prec_\pi \beta$, for $(\alpha, \beta) \in \pi$, and 
-   $\filter{\alpha} \bydef{=} \bsetdef{\beta \in (2^P \times
-    \guards{V} \times \updates{V})}{\alpha \prec_\pi \beta}$, for the set of
-  interactions that have higher priority than $\alpha$.
-\end{definition}
-
-\begin{definition}[Application of priority]
-  \label{defn:priority:sem}
-  The application of a priority model $\pi$ over $(V, P, \export)$
-  to a component $B = \tuple{Q, q^0, V, \val{0}{}, P, \export, \goesto{}}$
-  is the component $\pi(B) = \tuple{Q, q^0, V, \val{0}{}, P, \export,
-  \goesto[\pi]{}}$, where $\goesto[\pi]{}$ is the minimal transition
-  relation satisfying the rule (we denote
-  $\filter[q]{\alpha} \bydef{=} %% \filter{\alpha} \cap
-  %% \bsetdef{\beta \in (2^P \times \guards{V} \times \updates{V})}
-  \setdef{\beta \in \filter{\alpha}}{q \goesto{\beta}}$)
-%
-  \begin{equation*}
-    \label{eq:priority:sem}
-%
-    \infer{
-      \alpha = (a, g, u)
-      \and
-      q \goesto{a, g, u} q'
-      \and
-      \textstyle
-      g' = g \land \bigwedge_{(b, h, w) \in \filter[q]{\alpha}} \lnot h
-    }{
-      q \goesto[\pi]{a, g', u} q'
-    }\,.
-  \end{equation*}
-%
-  %% \todoSBin{Add the intuitive explanation}
-\end{definition}
-
-\addSB{Intuitively, an interaction can be fired only if all the
-higher-priority interactions available in the current state are
-disabled by their respective guards.}
-
-In this paper, we will only consider the so-called \emph{maximal
-  progress} priority $\mu$, where $(a, g, u) \prec_\mu (b, h, w)$ iff $a
-\varsubsetneq b$ (\ie $a \subseteq b$ and $a \neq b$).  In
-\secn{conclusion}, we discuss the possibility of generalising the
-obtained results to other priority models.
-%
-Below, we will assume that the maximal progress priority $\mu$ is
-applied after each composition with an interaction model.
-
-%% Finally, \emph{priorities}\mdash defined by a strict partial order on
-%% the set of possible interactions\mdash narrow the choice among the
-%% enabled interactions at any given round.  The default priority is the
-%% so-called \emph{maximal progress}, whereby among any two interactions
-%% $a \subset b$ (as sets of ports), $b$ has higher priority than $a$.
-In our running example, under the maximal progress priority, the
-port $\NameTimer.\PortTick$ will never fire alone in a global state,
-where the \noteSB{This turns out to be the first use of the word. I am tempted to pretend I did not notice.}\hl{dangling} port $\PortFail$ is also enabled.
-
-%% Adding priorities $\NameOprnd.\PortFinish < \NameCtrl.\PortReset$ and
-%% $\NameOprnd.\PortFinish < \NameOprnd.\PortResume$, ensures that, after
-%% a failure, the operation performed by $\NameOprnd$ cannot finish
-%% unless it is explicitly resumed or the system is reset.
-
-%% \begin{note}
-%%   \label{rem:maxprogress}
-%% \end{note}
-
-%% %****************************************************************
-%% \subsection{Running example: Failure Monitor architecture}
-%% \label{secn:failure-monitor}
-
-%\noteLH{Ludo ou simon: essayer de remonter la description generique en debut de section}
-
-%****************************************************************
-\subsubsection{Architectures}
-\label{secn:archi}
-
-Architectures are partially defined BIP models, where \emph{dangling}
-ports serve as placeholders for the eventual connection with
-additional \emph{operand} components.
-
-%% Contrary to standard BIP models, architectures comprise one or several
-%% \emph{operand} components, whereof only the set of \emph{ports} is
-%% given.  Here, the operand component is $\NameOprnd$ and its interface
-%% consists of the ports $\PortFinish$, $\PortResume$ and $\PortFail$.
-
-%% Application of the Failure Monitor architecture ensures that, whenever
-%% a failure is registered in the operand component, the system will be
-%% reset, unless a resumption is registered within $\mathrm{Max}$ time
-%% units (more details in Sect.~\ref{section:resultOA}).
-
-%% \noteLHin{should we say that always epsilon C is the epsilon of C?}
-
-\begin{definition}[Architecture]
-  \label{defn:arch}
-  An \emph{architecture} is a tuple $A = \tuple{\cC, V_A, P_A,
-    \export[A], \Gamma}$, where
-%  
-  \begin{itemize}
-\item
-  $\cC$ is a finite set of \emph{coordinating components},
-  %% with pairwise disjoint sets of ports and variables,
-  such that
-  $\bigcup_{C \in \cC} P_C \subseteq P_A$ and
-  $\bigcup_{C \in \cC} V_C \subseteq V_A$;
-%
-  ports in $P_A \setminus \bigcup_{C \in \cC} P_C$, which do not
-  belong to any of the coordinating components are called
-  \emph{dangling};
-
-\item
-  $\export[A] : P_A \rightarrow 2^{V_A}$ is an export function, such
-  that $\export[A](p) = \export[C](p)$, for any $C \in \cC$ and $p \in
-  P_C$ and $\export[A](p) \subseteq V_A \setminus \bigcup_{C \in \cC}
-  V_C$ for any dangling port $p$; and
-
-\item
-  $\Gamma \subseteq 2^{P_A} \times \guards{V_A} \times \updates{V_A}$
-  is an interaction model over $(V_A, P_A, \export[A])$.
-  \end{itemize}
-
-\end{definition}
-
-\begin{definition}[Application of an architecture]
-  \label{defn:arch:application}
-  Let $A = \tuple{\cC, V_A, P_A, \export[A], \Gamma}$ be an architecture and let $\cB$
-  be a set of components, such that
-  $V_A \subseteq V \bydef{=} \bigcup_{B \in \cB \cup \cC} V_B$,
-  $P_A \subseteq P \bydef{=} \bigcup_{B \in \cB \cup \cC} P_B$
-%
-  %% \begin{align}
-  %%   \bigcup_{B \in \cB} V_B \cap \bigcup_{C \in \cC} V_C = \emptyset\,,
-  %%   &&
-  %%   V_A \subseteq V \bydef{=} \bigcup_{B \in \cB \cup \cC} V_B\,,
-  %%   \\
-  %%   \bigcup_{B \in \cB} P_B \cap \bigcup_{C \in \cC} P_C = \emptyset\,,
-  %%   &&
-  %%   P_A \subseteq P \bydef{=} \bigcup_{B \in \cB \cup \cC} P_B\,,
-  %% \end{align}
-%
-  and $\export[A](p) = V_A \cap \export[B](p)$, for any $B \in \cB$
-  and $p \in P_A \cap P_B$.
-%
-  The \emph{application of the architecture $A$ to the set of
-  components $\cB$} is the component $ A(\cB) \bydef{=}
-  \mu\bigl((\IMextend{\Gamma}{P})(\cC \cup \cB)\bigr)$, where
-%
-  $\IMextend{\Gamma}{P} \bydef{=}
-  \bsetdef{
-    (a, g, u)
-  }{
-    a \subseteq P,
-    (a \cap P_A, g, u) \in \Gamma
-  }$
-  is
-  %% is the \emph{extension} of the interaction
-  %% model $\Gamma$ to the set of ports $P$, \ie
-  the interaction model
-  over $(V, P, \export)$, with
-  \[
-  \export(p) = 
-  \begin{cases}
-    \export[C](p), & \text{for all } C \in \cC, p \in P_C,
-    \\
-    \export[B](p), & \text{for all } B \in \cB, p \in P_B,
-  \end{cases}
-  \]
-%% defined by \noteLH{looks like this also depends on Pa}
-%% %
-%%   \noteSB{It does, indeed.  To be completely rigorous, I could replace
-%%     this with something like $\Gamma\uparrow_{P_A}^P$ but this is
-%%     quite heavy and the dependency is already implicit from the fact
-%%     that $\Gamma$ is defined on $P_A$}
-%% %
-%%   \noteSB{Which one of \eq{im:extension} and \eq{im:extension1} is
-%%     more intuitive?}
-%
-  %% \begin{align}
-  %%   \label{eq:im:extension}
-  %%   \IMextend{\Gamma}{P} &\bydef{=}
-  %%   \bsetdef{
-  %%     (a \cup a', g, e)
-  %%   }{
-  %%     (a, g, e) \in \Gamma, a' \subseteq P \setminus P_A
-  %%   }
-  %%   \\
-  %%   \label{eq:im:extension1}
-  %%   &= 
-  %%   \bsetdef{
-  %%     (a, g, e)
-  %%   }{
-  %%     a \subseteq P,
-  %%     (a \cap P_A, g, e) \in \Gamma
-  %%   }
-  %% \end{align}
-%
-  and $\mu$ is the maximal progress priority model.
-\end{definition}
-
-%% \todoSBin{Define equivalence $\arequiv$?}
-
-An architecture $A$ enforces coordination constraints on the
-components in $\cB$.  The interface $(V_A, P_A, \export[A])$ of an
-architecture $A$ contains all ports of the coordinating
-components $\cC$ and the dangling ports, which must belong to
-the components in $\cB$.  In the application $A(\cB)$, the ports
-belonging to $P_A$ can only participate in the interactions
-defined by the interaction model $\Gamma$ of $A$.  Ports which do
-not belong to $P_A$ are not restricted and can participate in any
-interaction.  %% In particular, they can join the interactions in
-%% $\Gamma$ (see \eq{im:extension}).  If the interface of the
-%% architecture covers all ports of the system, \ie $P = P_A$, we
-%% have $P\setminus P_A = \emptyset$ and the only interactions
-%% allowed in $A(\cB)$ are those belonging to $\Gamma$.  Notice also
-%% that the restrictions imposed by \defn{arch:application} on the
-%% set of operand components $\cB$ ensure that an interaction in
-%% $\IMextend{\Gamma}{P}$ can only refer to variables of the
-%% participating components.
-%
-%% Finally, 
-The definition of $\IMextend{\Gamma}{P}$ requires that
-an interaction from $\Gamma$ be involved in every interaction
-belonging to $\IMextend{\Gamma}{P}$.  To allow the ports from $P
-\setminus P_A$ to be fired independently in $A(\cB)$, one must
-have $(\emptyset, \true, \noop) \in \Gamma$.
-
-In our running example, there are four dangling ports.  Intuitively, the
-architecture monitors the activation of the dangling port {\PortFail}, then
-waits for a period comprised between $\mathrm{Min}$ and $\mathrm{Max}$
-and, unless {\PortResume} is activated, asks for a system reset
-through an invocation of the dangling port {\PortAsk}.
-
-\begin{definition}[Composition of architectures]
-  \label{defn:arch:composition}
-  Let $A_i = \tuple{\cC_i, V_{A_i}, P_{A_i}, \export[A_i], \Gamma_i}$, for $i = 1,2$,
-  be two architectures.  The \emph{composition} of $A_1$ and
-  $A_2$ is the architecture $A_1 \arcomp A_2 = \tuple{\cC_1 \cup \cC_2,
-  V_{A_1} \cup V_{A_2}, P_{A_1} \cup P_{A_2}, \export[A_1] \cup \export[A_2], \Gamma}$, where
-%
-  \begin{equation}
-    \label{eq:arch:composition}
-    \Gamma = \bsetdef{
-      (a, g^1 \land g^2, u^1 \expmix u^2) 
-    }{
-      (a \cap P_{A_i}, g^i, u^i) \in \Gamma_i,
-      \text{ for } i = 1,2
-    }
-    \,.
-  \end{equation}
-\end{definition}
-
-\begin{proposition}[Properties of $\arcomp$]
-  \label{prop:arcomp:nice}
-  %% Architecture composition
-  $\arcomp$ is associative and commutative.
-  %%; it is idempotent if all coordinating components
-  %% are deterministic; $A_{id} = \bigl(\emptyset, \emptyset,
-  %% \emptyset, \emptyset, \{(\emptyset, \true, \noop)\}\bigr)$ is its neutral element, \ie for
-  %% any architecture $A$, we have $A \oplus A_{id} \arequiv A$.
-  %% Furthermore, for any component $B$, we have $A_{id}(B) = \mu(B)$.
-\end{proposition}
-%
-\begin{proof}[Sketch of the proof]
-  %% Commutativity and associativity 
-  Follows from the corresponding
-  properties of set union, Boolean conjunction and
-  semilattice meet.
-%
-%% \todoLH{Check when equivalence is defined}
-%%   Suppose we have two architectures $A \arequiv A'$.  This does not
-%%   necessarily mean that their sets of coordinating components
-%%   coincide.  However, if all the involved coordinating components
-%%   are deterministic, then, in any state of $(A \arcomp A')(\cB)$,
-%%   both architectures will impose the same restrictions, enabling
-%%   the same interactions between the coordinating and operand
-%%   components.  Hence, we have $(A \arcomp A')(\cB) = A(\cB) =
-%%   A'(\cB)$.  Since this holds for any set of components $\cB$, we
-%%   conclude that $A \arcomp A' \arequiv A \arequiv A'$.
-%% %
-%%   The properties of $A_{id}$ follow immediately from the
-%%   definitions of architecture application and composition.
-\end{proof}
-
-%% The last statement of \prop{arcomp:nice} highlights a subtle point:
-%% $A_{id}$ is the neutral element of the $\arcomp$ operator\mdash it is
-%% not the identity operator on components.
-
-%****************************************************************
-\subsubsection{Preservation of safety properties}
-\label{secn:safety}
-
-For a component $B$, we denote $S_{\semopen{B}}$,
-$s^0_{\semopen{B}}$ the corresponding constituents of
-$\semopen{B}$.
-
-\begin{definition}[Properties]
-  \label{defn:property}
-  Let $B$ be a component.  A \emph{(safety) property} 
-  of $B$ is a predicate $\Phi$ on
-  $S_{\semopen{B}}$, such that $\bigl((q,
-  \val{}{}) \models \Phi\bigr) \land (\val[\primeit]{}{} \order
-  \val{}{})$ implies $(q, \val[\primeit]{}{}) \models \Phi$.
-  %% ,
-  %% where we write $(q, \val{}{}) \models \Phi$ iff $\Phi(q,
-  %% \val{}{}) = \true$.
-  A property $\Phi$ is \emph{initial} if
-  $s^0_{\semopen{B}} \models \Phi$.
-  %% \todoSB{Do we need this?}\hl{;
-  %% it is \emph{reachable} iff there exists a possibly empty path
-  %% $s^0_{\semopen{B}} \goesto{a^1, \val{1}{}} s^1 \goesto{a^2,
-  %%   \val{2}{}} \cdots \goesto{a^n, \val{n}{}} s^n$, such that
-  %% $s^n \models \Phi$}.
-\end{definition}
-
-\label{property:reset}
-\addSB{Although we define properties as state predicates, any
-  appropriate logic can be used to specify them.  For instance, the
-  property \emph{``There is always a possibility to reset the system
-    or resume operation after a single failure'' (\ie without
-    additional failures occuring in the meantime)} enforced by the
-  Failure Monitor architecture can be specified using CTL as $\AG
-  \bigl(\PortFail \rightarrow \EU[]{\lnot \PortFail}{(\PortResume \lor
-    \PortReset)}\bigr)$.  Additional properties are provided in
-  \app{properties}.}
-
-%% \todoSB{Cite the original paper somewhere.}
-The main idea of our approach is that an architecture enforces
-its characteristic property on the set of its operand components.
-From this point of view, the set of coordinating components is
-not relevant, neither are their states.  Thus, to talk about
-properties enforced by architectures, we consider properties on
-the unrestricted composition of the operand components as
-formalized by the following definition.
-
-\begin{definition}[Enforcing properties]
-  \label{defn:enforce}
-  Let $A = \tuple{\cC, P_A, V_A, \export[A], \Gamma}$ be an architecture; let $\cB$
-  be a set of components and $\Phi$ an initial property of
-  their parallel composition $\Gamma_{\|}(\cB)$,
-  with $\Gamma_{\|} = \setdef{(a,\true,\emptyset)}{a \subseteq \bigcup_{B \in \cB} P_B}$.
-  We say that \emph{$A$ enforces $\Phi$ on
-    $\cB$} iff, for every state $s = (s_c, s_b)$ reachable in
-  $\semopen{A(\cB)}$, with 
-  $s_c \in \prod_{C \in \cC} S_{\semopen{C}}$ and
-  $s_b \in \prod_{B \in \cB} S_{\semopen{B}}$,
-  we have $s_b \models \Phi$.
-\end{definition}
-
-According to the above definition, when we say that an
-architecture enforces some property $\Phi$, it is implicitly
-assumed that $\Phi$ is initial for the coordinated components.
-Below, we omit mentioning this explicitly.
-
-\defn{up:compat} in \secn{arch:appendix} provides a formal definition
-of the notion of \emph{upwards compatibility}, which we present here
-informally due to page limitations.  Two architectures $A_1$ and $A_2$
-are said to be upwards compatible iff, whenever their composition
-involves the fusion of two interactions $a_1 = a \cap P_{A_1}$ and
-$a_2 = a \cap P_{A_2}$ (see \eq{arch:composition}), whereof one, say
-$a_1$, is inhibited in a given state by a larger interaction $b_1
-\supset a_1$, there exists an interaction $b_2 \supseteq a_2$ that can
-be fused with $b_1$ to form an interaction enabled in the same state.
-
-\begin{theorem}[Preserving enforced properties]
-  \label{thm:combining}
-  Let $\cB$ be a set of components; let $A_i = \tuple{\cC_i, V_{A_i},
-  P_{A_i}, \export[A_i], \Gamma_i}$, for $i = 1,2$, be two upwards compatible architectures
-  enforcing on $\cB$ the properties $\Phi_1$ and $\Phi_2$
-  respectively.  The composition $A_1 \arcomp A_2$ enforces on
-  $\cB$ the property $\Phi_1 \land \Phi_2$.
-\end{theorem}
-
-%****************************************************************
 %****************************************************************
@@
 %****************************************************************
+%****************************************************************
+
+\section{The theory of architectures with data}
+\label{secn:archs}
+
+%****************************************************************
+
+\subsubsection{Components and composition}
+\label{secn:components}
+
+%% \noteSBin{%
+%% To guarantee preservation of properties guards and expressions
+%% have to be \emph{monotonic}.  In the case of a trivial order, \ie
+%% when nothing is comparable, \emph{any guard or expression is
+%%   monotonic}.  Thus, this is not really a constraint!
+
+%% Do we put this in the definition of expressions and guards or in
+%% the definitions of components and interaction models?
+%% }
+
+\begin{definition}[Components]
+  \label{defn:component}
+  A \emph{component} is a tuple $\tuple{Q, q^0, V, \val{0}{}, P,
+  \export, \goesto{}}$, where
+  \begin{itemize}
+  \item $Q$ is a set of \emph{states}, with $q^0 \in Q$ the
+    \emph{initial state}, 
+  \item $V$ is a set of \emph{component variables},
+  \item $\val{0}{} : V \rightarrow \data$ is an \emph{initial
+    valuation} of the component variables, 
+  \item $P$ is a set of \emph{ports}, with
+    $\export : P \rightarrow 2^V$ 
+    the \emph{set of variables exported by each port},
+  \item $\goesto{}\, \subseteq
+    Q \times (2^P\setminus \{\emptyset\}) \times \guards{V} \times \updates{V} \times Q$
+%
+    is a \emph{transition relation}, with transitions
+    labelled by \emph{interactions}, \ie triples consisting of a non-empty set of ports,
+    %% $\emptyset \neq a \subseteq P$,
+    a monotonic Boolean \emph{guard}
+    %% $g \in \guards{V}$ 
+    and a monotonic \emph{update assignment}.
+    %% \hl{$u \in \updates{V}$}.
+  \end{itemize}
+%
+  We call the triple $(V,P, \export)$ the \emph{interface} of the
+  component.\,\footnote{%
+%
+  In practice, only exported variables, \ie those in the set
+  $\bigcup_{p \in P}\export(p)$, belong to the component interface and
+  can be used for the interactions with other components (see
+  \defn{im}).  However, in the context of this paper we can simplify
+  by omitting this separation.
+%
+  }
+%
+  Notations $q \goesto{a, g, u} q'$ and $q \goesto{a, g, u}$ are as usual;
+  for a component $B$, we denote $Q_B$, $q^0_B$, $V_B$, $\val{0}{B}$, $P_B$,
+  and $\export[B]$ the corresponding constituents of $B$.  We will
+  skip the index on the transition relations $\goesto{}$, since it
+  is always clear from the context.
+\end{definition}
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=0.9\columnwidth]{BIPspec-ArchFailureTimerMax-v4}
+  \caption{The BIP specification of the Failure Monitor architecture}
+  \label{fig:schema:ArchFailure:BIP}
+\end{figure}
+
+In this paper, we will use a running example, which is a refined
+version of the Failure Monitor architecture
+from~\cite{CubETH-case-study}.  Although \fig{schema:ArchFailure:BIP}
+shows the full definition of this architecture, we will explain its
+various elements progressively, as we define the corresponding
+notions.
+
+The model in \fig{schema:ArchFailure:BIP} has  components
+%% The
+%% component $\NameOprnd$ is an \emph{operand} of the architecture, \ie
+%% it only has its interface defined: $(\emptyset, \{\PortFinish,
+%% \PortResume, \PortFail\}, \export[\emptyset])$, with
+%% $\export[\emptyset](p) = \emptyset$, for all $p \in \{\PortFinish,
+%% \PortResume, \PortFail\}$.  
+%% The other two components,
+%
+$\NameTimer$(imer) and $\NameCtrl$(ontrol), with interfaces
+$\btuple{
+  \{t, z\},
+  \{\PortTick, \PortCancel, \PortTOT\},
+  \bigl\{\PortTick \mapsto \{t, z\}\bigr\}
+}$,
+and
+$\btuple{
+  \{\mathit{zone}\},
+  \{\PortReset, \PortFail, \PortResume, \PortTOC\},
+  \bigl\{\PortFail \mapsto \{\mathit{zone}\}\bigr\}
+}$, respectively.
+%
+%% \[
+%% \begin{array}{@{}c@{\hspace{3mm}}c@{}}
+%%   \bigl(
+%%   \{t, z\},
+%%   \{\PortTick, \PortCancel, \PortTOT\},
+%%   \export[\NameTimer]
+%%   \bigr)\,,
+%%   %% \qquad
+%%   &
+%%   \bigl(
+%%   \{\mathit{zone}\},
+%%   \{\PortReset, \PortFail, \PortResume, \PortTOC\},
+%%   \export[\NameCtrl]
+%%   \bigr)\,,
+%%   \\
+%%   \export[\NameTimer](p) =
+%%   \begin{cases}
+%%     \{t, z\}, & \text{if } p = \PortTick,\\
+%%     \emptyset, & \text{otherwise,}
+%%   \end{cases}
+%%   %% \]
+%%   %% and
+%%   %% \[
+%%   %% \quad
+%%   &
+%%   \export[\NameCtrl](p) =
+%%   \begin{cases}
+%%     \{\mathit{zone}\}, & \text{if } p = \PortFail,\\
+%%     \emptyset, & \text{otherwise.}
+%%   \end{cases}
+%% \end{array}
+%% \]
+%
+%% , where $\export[\NameCtrl](\PortFail) =
+%% \{\mathit{zone}\}$ and $\export[\NameCtrl](p) = \emptyset$, for all
+%% other ports $p$; $\export[\NameTimer](\PortTick) = \{t, z\}$ and
+%% $\export[\NameTimer](p) = \emptyset$, for all other ports $p$.
+Variable $t$ is implicitly assumed to be an integer.  Variables $z$
+and $\mathit{zone}$ are implicitly assumed to be integer intervals of
+the form $[l,u]$.  For both types, we also implicitly assume the
+natural ordering: increasing integers and interval inclusion.
+
+%% are \emph{coordinators}\mdash they are specified
+%% completely, including the states and transitions defining their
+%% \emph{behaviour}.
+Component \emph{behaviour} is defined by states %% ($\{\cstate{0},
+%% \cstate{1}, \cstate{2}\}$, for $\NameCtrl$; $\{\tstate{0}\}$, for
+%% $\NameTimer$)
+and transitions.
+The initial states
+\tstate{0} and \cstate{0}, and valuations $\val{0}{\NameTimer} = \{t
+\mapsto 0, z \mapsto \topinterval\}$ and $\val{0}{\NameCtrl} =
+\{\mathit{zone} \mapsto [\mathrm{Min}, \mathrm{Max}]\}$ are shown by
+the incoming arrows $\goesto{\TimerInit[]} \tstate{0}$ and
+$\goesto{\IntervalInit[]} \cstate{0}$.\footnote{%
+%
+  We use $\topinterval$ to denote the top interval in the inclusion
+  order, \ie $(-\infty, +\infty)$.
+%
+} The constants $\mathrm{Min}$ and $\mathrm{Max}$ are the parameters
+of the architecture.
+
+Transitions are labelled with ports of the
+corresponding components, Boolean guards and update assignments on local
+variables.  \Eg[,] the loop transition $\tstate{0}
+\goesto{\PortTick, \GuardTick[], \TimerUpd[]} \tstate{0}$ in the
+component $\NameTimer$ is labeled by the port $\PortTick$.  It can be
+fired only when the current value of the local variable $t$ is less
+than $z.u$.
+%% , where $z = [l, u]$ is a local variable representing an
+%% interval
+Upon firing, this transition increments the value of $t$ by $1$.  The
+guards and update assignments of the transitions of $\NameCtrl$ are
+omitted.  The default values are the constant predicate $\true$ (true) and
+the empty assignment {\noop}, respectively.  
+%\noteLH{It looks like Max is in zone, I do not understand}
+%
+Clearly, all guards and update assignments are monotonic.
+
+%% \todoSBin{Speak of guard monotonicity}
+
+\begin{definition}[Component semantics]
+  \label{defn:comp:semantics}
+  The \emph{semantics} of a component $B = \tuple{Q, q^0, V,
+  \val{0}{}, P, \export, \goesto{}}$ is %% given by
+  the LTS denoted $\semopen{B} = \tuple{S,
+  s^0, \goesto{}}$, where $S = Q \times \valuations{V}$, $s^0 =
+  \tuple{q^0, \val{0}{}}$ and $\goesto{}$ is the minimal transition
+  relation satisfying the rule
+  %
+  \begin{equation}
+    \label{eq:comp:semantics}
+    \infer{
+      q \goesto{a, g, u} q'
+      \and
+      \val{}{} \models g
+      \and
+      \val[\primeit]{}{} = \tilde{\val{}{}}[u]
+      \and
+      \valdiff{\val{}{}}{\tilde{\val{}{}}} \subseteq \export(a)
+    }{
+      (q, \val{}{}) \goesto{a,\tilde{\val{}{}}} (q', \val[\primeit]{}{})
+    }
+    \,.
+  \end{equation}
+  %
+  %% \todoSB{Do we actually need this?}\todoLH{I agree: I do not think we need this}
+  %% \hl{The \emph{closed semantics} of $B$ is given by the LTS denoted
+  %% $\semclosed{B} \bydef{=}\reachable{\semopen{B}}$, comprising
+  %% only the reachable states of $\semopen{B}$.}
+\end{definition}
+
+The use of the intermediate valuation $\tilde{\val{}{}}$ in the
+conclusion and the third premise of rule \eq{comp:semantics}
+allows some of the variables to get new values before the
+transition is actually fired.  Thus the component is \emph{open}
+to the exchange of data with its environment.  However, the
+fourth premise in \eq{comp:semantics} restricts the set of
+variables, which can be affected by such data transfer, to those
+that are exported through the ports participating in the
+interaction.
+
+\begin{definition}[Interaction model]
+  \label{defn:im}
+  For a finite set of component interfaces $(V_i, P_i,
+  \export[i])^{i \in I}$, such that all $P_i$ and all $V_i$ are
+  pairwise disjoint, %% \ie $\forall i \neq j,\ P_i \cap P_j = V_i \cap
+  %% V_j = \emptyset$. 
+  let $P = \bigcup_{i \in I} P_i$, $V = \bigcup_{i
+    \in I} V_i$ and $\export : P \rightarrow 2^V$ such that, for any
+  $p \in P_i$, $\export(p) = \export[i](p)$. 
+%
+  %% \noteSB{Updated this}\hl{and $V_a \bydef{=} \bigcup_{i \in
+  %%   \supp{a}} \export[i](a \cap P_i)$ the set of component
+  %% variables exported through $a$.}
+
+  An \emph{interaction model over $(V, P, \export)$} is a set $\Gamma
+  \subseteq 2^P \times \guards{V} \times \updates{V}$, such that,
+  for any interaction $(a, g, u) \in \Gamma$, we have
+  $g \in \guards{\export(a)}$ and $e \in \updates{\export(a)}$.\footnote{%
+%
+    Notice that this definition allows $(\emptyset, \true,
+    \noop)$ and $(\emptyset, \false, \noop)$ to be included in
+    $\Gamma$.
+%
+  }
+  %% We call the set of ports $P$ the \emph{domain} of the
+  %% interaction model.
+\end{definition}
+
+%% \noteLH{supp should go outside the definition}
+When speaking of a set of components or interfaces, we will always
+assume that it satisfies the disjointness assumption of \defn{im}.
+%
+We call the \emph{support} of a set of ports $a \subseteq P$, denoted
+$\supp{a}$, either the set $\setdef{i \in I}{a \cap P_i \neq
+  \emptyset}$ (for $P = \bigcup_{i=1}^n P_i$) or the set $\setdef{B
+  \in \cB}{a \cap P_B \neq \emptyset}$ (for $P = \bigcup_{B \in \cB}
+P_B$).  The precise meaning of this notation will always be clear from
+the context.  Intuitively, for an interaction $(a, g, u)$, $\supp{a}$
+denotes the set of the participating components.
+
+\begin{definition}[Composition]
+  \label{defn:im:sem}
+  The \emph{composition} of a finite set of components $\cB = \tuple{Q_i,
+  q^0_i, V_i, \val{0}{i}, P_i, \export[i], \goesto{}}^{i \in I}$ with
+  the interaction model $\Gamma$ over $\tuple{V, P, \export}$ (as in \defn{im})
+  is the component $\Gamma(\cB) = \tuple{Q, q^0, V, \val{0}{}, P,
+    \export, \goesto{}}$, where
+%
+  $Q = \prod_{i \in I} Q_i$;
+%
+  $q^0 = (q_i^0)^{i \in I}$;
+%
+  $\val{0}{}: V \rightarrow \data$ is such that, for any $v \in
+  V_i$, $\val{0}{}(v) = \val{0}{i}(v)$;
+%
+  and $\goesto{}$ is the minimal transition relation satisfying
+  the rule
+%
+  \begin{gather*}
+%%     \label{eq:im:empty}
+%%     \infer{
+%%       q_j \goesto{\emptyset, g, e} q_j'
+%%       \and
+%%       \forall i \neq j, q_i = q_i'
+%%     }{
+%%       (q_i)^{i \in I} \goesto{\emptyset, g, e} (q_i')^{i \in I}
+%%     }\,,
+%% %
+%%     \\[0.5\baselineskip]
+    \label{eq:im:sem}
+%
+    \infer{    
+      (a, g, u) \in \Gamma
+      \and
+      a \neq \emptyset
+      \and
+      \forall i \in \supp{a}, q_i \goesto{a \cap P_i, g_i, u_i} q_i'
+      \and
+      \forall i \not\in \supp{a}, q_i = q_i'
+%
+      \\\\
+      \textstyle
+%
+      g' = g \land \bigwedge_{i \in \supp{a}} g_i
+      \and
+      u' = u; u_i^{i \in \supp{a}}
+    }{
+      (q_i)^{i \in I} \goesto{a, g', u'} (q_i')^{i \in I}
+    }\,.
+  \end{gather*}
+  %% \todoSBin{Add the intuitive explanation}
+\end{definition}
+
+\addSB{Intuitively, an interaction can be fired if all the involved
+  components are ready to fire their corresponding transitions.  The
+  other components do not change their states.  Both the interaction
+  guard and those of the participating transitions must be satisfied.
+  The update assignment of the interaction is executed first, followed
+  by those of the components.}
+
+Specifying interaction models as sets of sets of ports is not
+practical due to their potentially exponential size.  An algebra of
+connectors was introduced in \cite{BliSif08-acp-tc} in order to
+structure interactions in BIP models.
+
+Connectors are hierarchical, tree-like structures with component ports
+at the leaves.  They define sets of interactions, based on the
+attributes of the nodes, which may be either \emph{trigger}
+(triangles in \fig{schema:ArchFailure:BIP}) or \emph{synchron}
+(bullets in \fig{schema:ArchFailure:BIP}).
+%
+If all sub-connectors of a connector are synchrons, then an
+interaction is allowed by the connector only if each subconnector
+can contribute.
+%
+If at least one of the sub-connectors is a trigger, then any
+interaction consisting of contributions of any set of sub-connectors
+\emph{involving at least one of the triggers} is allowed.
+%
+The interaction model is defined as the set of all interactions
+allowed by at least one of the connectors in the system.
+%% The composition semantics of BIP systems consists in
+%% firing exactly one interaction, enabled through at least one of the
+%% top-level connectors, at each execution round.
+
+For instance, the connector {\NameTimer.\PortTick
+  \trigsynch (\PortFail \trigsynch \NameCtrl.\PortFail)} is a
+two-level hierarchical connector.  In the second-level subconnector
+{\PortFail \trigsynch \NameCtrl.\PortFail}, the port {\PortFail} is a
+trigger, whereas {\NameCtrl.\PortFail} is a synchron.  Therefore, this
+subconnector allows two interactions labelled $\{\PortFail\}$ and $\listset{\NameCtrl.\PortFail, \PortFail}$.  Similarly, at the top level,
+{\NameTimer.\PortTick} is a trigger, whereas the second-level
+subconnector is a synchron.  Hence, the overall connector allows the
+interaction involving only one port {\NameTimer.\PortTick}\footnote{%
+%
+  Such interactions are called \emph{singleton interactions}.
+%
+} and any interaction involving both {\NameTimer.\PortTick} and
+\emph{some} interaction of the second-level subconnector.  Combining
+the two levels we can see that the entire connector defines the
+following three interactions (observe that $\topinterval +
+\NameTimer.t = \topinterval$ and $\NameTimer.z \cap \topinterval =
+\NameTimer.z$):
+%
+\begin{gather*}
+  \bigl(\{\NameTimer.\PortTick\},
+  \true, \emptyset\bigr)
+  %% \NameTimer.z := \NameTimer.z\bigr)
+  ,
+%
+  \qquad
+%
+  \bigl(\{\PortFail, \NameTimer.\PortTick\},
+  \true, \emptyset\bigr)
+  %% \NameTimer.z := \NameTimer.z\bigr)
+  ,
+%
+  \\
+%
+  \bigl(\{\NameCtrl.\PortFail, \PortFail, \NameTimer.\PortTick \},
+  \true,
+  \NameTimer.z := \NameTimer.z \cap (\NameCtrl.\mathit{zone} + \NameTimer.t)\bigr)
+  .
+\end{gather*}
+%% \begin{align*}
+%%   \bigl(\{\NameTimer.\PortTick\}&,
+%%   \true, 
+%%   \NameTimer.z := \NameTimer.z\bigr)
+%%   \,,\\
+%%   \bigl(\{\PortFail, \NameTimer.\PortTick\}&,
+%%   \true,
+%%   \NameTimer.z := \NameTimer.z\bigr)
+%%   \,,\\
+%%   \bigl(\{\NameCtrl.\PortFail, \PortFail, \NameTimer.\PortTick \}&,
+%%   \true,
+%%   \NameTimer.z := \NameTimer.z \cap (\NameCtrl.\mathit{zone} + \NameTimer.t)\bigr)
+%%   \,.
+%% \end{align*}
+
+%% \todoSB{Update this}
+%% \hl{For instance, in \fig{schema:ArchFailure:BIP}, the two ports
+%% $\NameTimer.\PortStart$ and $\NameCtrl.\PortFail$ are always
+%% synchronised, since they belong to exactly one binary sub-connector,
+%% where they are both synchrons.  In particular, this means that
+%% whenever the transition \cstate{0} \goesto{\PortFail} \cstate{1} is
+%% fired, so is the transition \tstate{0} \goesto{\PortStart,
+%%   \TimerInit[]} \tstate{1}, initialising the timer.  The binary
+%% connector $\NameTimer.\PortStart \twosynch
+%% \NameCtrl.\PortFail$ is a sub-connector of a hierarchical connector,
+%% where the port $\NameOprnd.\PortFail$ is a trigger.  Thus, the above
+%% interaction can only happen together with $\NameOprnd.\PortFail$,
+%% forming a ternary interaction.  On the contrary, being a trigger, the
+%% port $\NameOprnd.\PortFail$ can fire alone, forming a singleton
+%% interaction.}
+
+%% \todoSBin{Speak of data transfer}
+
+%% \todoSBin{Provide the interaction model}
+
+\begin{definition}[Priority model]
+  \label{defn:priority}
+  A \emph{priority model} over a component interface $(V, P,
+  \export)$\footnote{%
+%
+    Notice that the export function $\export$ has no impact on the
+    priority model definition.
+%
+  } is a strict partial order on interactions: $\pi
+  \subseteq \bigl(2^P \times \guards{V} \times \updates{V} \bigr)^2$.
+
+  We write $\alpha \prec_\pi \beta$, for $(\alpha, \beta) \in \pi$, and 
+   $\filter{\alpha} \bydef{=} \bsetdef{\beta \in (2^P \times
+    \guards{V} \times \updates{V})}{\alpha \prec_\pi \beta}$, for the set of
+  interactions that have higher priority than $\alpha$.
+\end{definition}
+
+\begin{definition}[Application of priority]
+  \label{defn:priority:sem}
+  The application of a priority model $\pi$ over $(V, P, \export)$
+  to a component $B = \tuple{Q, q^0, V, \val{0}{}, P, \export, \goesto{}}$
+  is the component $\pi(B) = \tuple{Q, q^0, V, \val{0}{}, P, \export,
+  \goesto[\pi]{}}$, where $\goesto[\pi]{}$ is the minimal transition
+  relation satisfying the rule (we denote
+  $\filter[q]{\alpha} \bydef{=} %% \filter{\alpha} \cap
+  %% \bsetdef{\beta \in (2^P \times \guards{V} \times \updates{V})}
+  \setdef{\beta \in \filter{\alpha}}{q \goesto{\beta}}$)
+%
+  \begin{equation*}
+    \label{eq:priority:sem}
+%
+    \infer{
+      \alpha = (a, g, u)
+      \and
+      q \goesto{a, g, u} q'
+      \and
+      \textstyle
+      g' = g \land \bigwedge_{(b, h, w) \in \filter[q]{\alpha}} \lnot h
+    }{
+      q \goesto[\pi]{a, g', u} q'
+    }\,.
+  \end{equation*}
+%
+  %% \todoSBin{Add the intuitive explanation}
+\end{definition}
+
+\addSB{Intuitively, an interaction can be fired only if all the
+higher-priority interactions available in the current state are
+disabled by their respective guards.}
+
+In this paper, we will only consider the so-called \emph{maximal
+  progress} priority $\mu$, where $(a, g, u) \prec_\mu (b, h, w)$ iff $a
+\varsubsetneq b$ (\ie $a \subseteq b$ and $a \neq b$).  In
+\secn{conclusion}, we discuss the possibility of generalising the
+obtained results to other priority models.
+%
+Below, we will assume that the maximal progress priority $\mu$ is
+applied after each composition with an interaction model.
+
+%% Finally, \emph{priorities}\mdash defined by a strict partial order on
+%% the set of possible interactions\mdash narrow the choice among the
+%% enabled interactions at any given round.  The default priority is the
+%% so-called \emph{maximal progress}, whereby among any two interactions
+%% $a \subset b$ (as sets of ports), $b$ has higher priority than $a$.
+In our running example, under the maximal progress priority, the
+port $\NameTimer.\PortTick$ will never fire alone in a global state,
+where the \noteSB{This turns out to be the first use of the word. I am tempted to pretend I did not notice.}\hl{dangling} port $\PortFail$ is also enabled.
+
+%% Adding priorities $\NameOprnd.\PortFinish < \NameCtrl.\PortReset$ and
+%% $\NameOprnd.\PortFinish < \NameOprnd.\PortResume$, ensures that, after
+%% a failure, the operation performed by $\NameOprnd$ cannot finish
+%% unless it is explicitly resumed or the system is reset.
+
+%% \begin{note}
+%%   \label{rem:maxprogress}
+%% \end{note}
+
+%% %****************************************************************
+%% \subsection{Running example: Failure Monitor architecture}
+%% \label{secn:failure-monitor}
+
+%\noteLH{Ludo ou simon: essayer de remonter la description generique en debut de section}
+
+%****************************************************************
+\subsubsection{Architectures}
+\label{secn:archi}
+
+Architectures are partially defined BIP models, where \emph{dangling}
+ports serve as placeholders for the eventual connection with
+additional \emph{operand} components.
+
+%% Contrary to standard BIP models, architectures comprise one or several
+%% \emph{operand} components, whereof only the set of \emph{ports} is
+%% given.  Here, the operand component is $\NameOprnd$ and its interface
+%% consists of the ports $\PortFinish$, $\PortResume$ and $\PortFail$.
+
+%% Application of the Failure Monitor architecture ensures that, whenever
+%% a failure is registered in the operand component, the system will be
+%% reset, unless a resumption is registered within $\mathrm{Max}$ time
+%% units (more details in Sect.~\ref{section:resultOA}).
+
+%% \noteLHin{should we say that always epsilon C is the epsilon of C?}
+
+\begin{definition}[Architecture]
+  \label{defn:arch}
+  An \emph{architecture} is a tuple $A = \tuple{\cC, V_A, P_A,
+    \export[A], \Gamma}$, where
+%  
+  \begin{itemize}
+\item
+  $\cC$ is a finite set of \emph{coordinating components},
+  %% with pairwise disjoint sets of ports and variables,
+  such that
+  $\bigcup_{C \in \cC} P_C \subseteq P_A$ and
+  $\bigcup_{C \in \cC} V_C \subseteq V_A$;
+%
+  ports in $P_A \setminus \bigcup_{C \in \cC} P_C$, which do not
+  belong to any of the coordinating components are called
+  \emph{dangling};
+
+\item
+  $\export[A] : P_A \rightarrow 2^{V_A}$ is an export function, such
+  that $\export[A](p) = \export[C](p)$, for any $C \in \cC$ and $p \in
+  P_C$ and $\export[A](p) \subseteq V_A \setminus \bigcup_{C \in \cC}
+  V_C$ for any dangling port $p$; and
+
+\item
+  $\Gamma \subseteq 2^{P_A} \times \guards{V_A} \times \updates{V_A}$
+  is an interaction model over $(V_A, P_A, \export[A])$.
+  \end{itemize}
+
+\end{definition}
+
+\begin{definition}[Application of an architecture]
+  \label{defn:arch:application}
+  Let $A = \tuple{\cC, V_A, P_A, \export[A], \Gamma}$ be an architecture and let $\cB$
+  be a set of components, such that
+  $V_A \subseteq V \bydef{=} \bigcup_{B \in \cB \cup \cC} V_B$,
+  $P_A \subseteq P \bydef{=} \bigcup_{B \in \cB \cup \cC} P_B$
+%
+  %% \begin{align}
+  %%   \bigcup_{B \in \cB} V_B \cap \bigcup_{C \in \cC} V_C = \emptyset\,,
+  %%   &&
+  %%   V_A \subseteq V \bydef{=} \bigcup_{B \in \cB \cup \cC} V_B\,,
+  %%   \\
+  %%   \bigcup_{B \in \cB} P_B \cap \bigcup_{C \in \cC} P_C = \emptyset\,,
+  %%   &&
+  %%   P_A \subseteq P \bydef{=} \bigcup_{B \in \cB \cup \cC} P_B\,,
+  %% \end{align}
+%
+  and $\export[A](p) = V_A \cap \export[B](p)$, for any $B \in \cB$
+  and $p \in P_A \cap P_B$.
+%
+  The \emph{application of the architecture $A$ to the set of
+  components $\cB$} is the component $ A(\cB) \bydef{=}
+  \mu\bigl((\IMextend{\Gamma}{P})(\cC \cup \cB)\bigr)$, where
+%
+  $\IMextend{\Gamma}{P} \bydef{=}
+  \bsetdef{
+    (a, g, u)
+  }{
+    a \subseteq P,
+    (a \cap P_A, g, u) \in \Gamma
+  }$
+  is
+  %% is the \emph{extension} of the interaction
+  %% model $\Gamma$ to the set of ports $P$, \ie
+  the interaction model
+  over $(V, P, \export)$, with
+  \[
+  \export(p) = 
+  \begin{cases}
+    \export[C](p), & \text{for all } C \in \cC, p \in P_C,
+    \\
+    \export[B](p), & \text{for all } B \in \cB, p \in P_B,
+  \end{cases}
+  \]
+%% defined by \noteLH{looks like this also depends on Pa}
+%% %
+%%   \noteSB{It does, indeed.  To be completely rigorous, I could replace
+%%     this with something like $\Gamma\uparrow_{P_A}^P$ but this is
+%%     quite heavy and the dependency is already implicit from the fact
+%%     that $\Gamma$ is defined on $P_A$}
+%% %
+%%   \noteSB{Which one of \eq{im:extension} and \eq{im:extension1} is
+%%     more intuitive?}
+%
+  %% \begin{align}
+  %%   \label{eq:im:extension}
+  %%   \IMextend{\Gamma}{P} &\bydef{=}
+  %%   \bsetdef{
+  %%     (a \cup a', g, e)
+  %%   }{
+  %%     (a, g, e) \in \Gamma, a' \subseteq P \setminus P_A
+  %%   }
+  %%   \\
+  %%   \label{eq:im:extension1}
+  %%   &= 
+  %%   \bsetdef{
+  %%     (a, g, e)
+  %%   }{
+  %%     a \subseteq P,
+  %%     (a \cap P_A, g, e) \in \Gamma
+  %%   }
+  %% \end{align}
+%
+  and $\mu$ is the maximal progress priority model.
+\end{definition}
+
+%% \todoSBin{Define equivalence $\arequiv$?}
+
+An architecture $A$ enforces coordination constraints on the
+components in $\cB$.  The interface $(V_A, P_A, \export[A])$ of an
+architecture $A$ contains all ports of the coordinating
+components $\cC$ and the dangling ports, which must belong to
+the components in $\cB$.  In the application $A(\cB)$, the ports
+belonging to $P_A$ can only participate in the interactions
+defined by the interaction model $\Gamma$ of $A$.  Ports which do
+not belong to $P_A$ are not restricted and can participate in any
+interaction.  %% In particular, they can join the interactions in
+%% $\Gamma$ (see \eq{im:extension}).  If the interface of the
+%% architecture covers all ports of the system, \ie $P = P_A$, we
+%% have $P\setminus P_A = \emptyset$ and the only interactions
+%% allowed in $A(\cB)$ are those belonging to $\Gamma$.  Notice also
+%% that the restrictions imposed by \defn{arch:application} on the
+%% set of operand components $\cB$ ensure that an interaction in
+%% $\IMextend{\Gamma}{P}$ can only refer to variables of the
+%% participating components.
+%
+%% Finally, 
+The definition of $\IMextend{\Gamma}{P}$ requires that
+an interaction from $\Gamma$ be involved in every interaction
+belonging to $\IMextend{\Gamma}{P}$.  To allow the ports from $P
+\setminus P_A$ to be fired independently in $A(\cB)$, one must
+have $(\emptyset, \true, \noop) \in \Gamma$.
+
+In our running example, there are four dangling ports.  Intuitively, the
+architecture monitors the activation of the dangling port {\PortFail}, then
+waits for a period comprised between $\mathrm{Min}$ and $\mathrm{Max}$
+and, unless {\PortResume} is activated, asks for a system reset
+through an invocation of the dangling port {\PortAsk}.
+
+\begin{definition}[Composition of architectures]
+  \label{defn:arch:composition}
+  Let $A_i = \tuple{\cC_i, V_{A_i}, P_{A_i}, \export[A_i], \Gamma_i}$, for $i = 1,2$,
+  be two architectures.  The \emph{composition} of $A_1$ and
+  $A_2$ is the architecture $A_1 \arcomp A_2 = \tuple{\cC_1 \cup \cC_2,
+  V_{A_1} \cup V_{A_2}, P_{A_1} \cup P_{A_2}, \export[A_1] \cup \export[A_2], \Gamma}$, where
+%
+  \begin{equation}
+    \label{eq:arch:composition}
+    \Gamma = \bsetdef{
+      (a, g^1 \land g^2, u^1 \expmix u^2) 
+    }{
+      (a \cap P_{A_i}, g^i, u^i) \in \Gamma_i,
+      \text{ for } i = 1,2
+    }
+    \,.
+  \end{equation}
+\end{definition}
+
+\begin{proposition}[Properties of $\arcomp$]
+  \label{prop:arcomp:nice}
+  %% Architecture composition
+  $\arcomp$ is associative and commutative.
+  %%; it is idempotent if all coordinating components
+  %% are deterministic; $A_{id} = \bigl(\emptyset, \emptyset,
+  %% \emptyset, \emptyset, \{(\emptyset, \true, \noop)\}\bigr)$ is its neutral element, \ie for
+  %% any architecture $A$, we have $A \oplus A_{id} \arequiv A$.
+  %% Furthermore, for any component $B$, we have $A_{id}(B) = \mu(B)$.
+\end{proposition}
+%
+\begin{proof}[Sketch of the proof]
+  %% Commutativity and associativity 
+  Follows from the corresponding
+  properties of set union, Boolean conjunction and
+  semilattice meet.
+%
+%% \todoLH{Check when equivalence is defined}
+%%   Suppose we have two architectures $A \arequiv A'$.  This does not
+%%   necessarily mean that their sets of coordinating components
+%%   coincide.  However, if all the involved coordinating components
+%%   are deterministic, then, in any state of $(A \arcomp A')(\cB)$,
+%%   both architectures will impose the same restrictions, enabling
+%%   the same interactions between the coordinating and operand
+%%   components.  Hence, we have $(A \arcomp A')(\cB) = A(\cB) =
+%%   A'(\cB)$.  Since this holds for any set of components $\cB$, we
+%%   conclude that $A \arcomp A' \arequiv A \arequiv A'$.
+%% %
+%%   The properties of $A_{id}$ follow immediately from the
+%%   definitions of architecture application and composition.
+\end{proof}
+
+%% The last statement of \prop{arcomp:nice} highlights a subtle point:
+%% $A_{id}$ is the neutral element of the $\arcomp$ operator\mdash it is
+%% not the identity operator on components.
+
+%****************************************************************
+\subsubsection{Preservation of safety properties}
+\label{secn:safety}
+
+For a component $B$, we denote $S_{\semopen{B}}$,
+$s^0_{\semopen{B}}$ the corresponding constituents of
+$\semopen{B}$.
+
+\begin{definition}[Properties]
+  \label{defn:property}
+  Let $B$ be a component.  A \emph{(safety) property} 
+  of $B$ is a predicate $\Phi$ on
+  $S_{\semopen{B}}$, such that $\bigl((q,
+  \val{}{}) \models \Phi\bigr) \land (\val[\primeit]{}{} \order
+  \val{}{})$ implies $(q, \val[\primeit]{}{}) \models \Phi$.
+  %% ,
+  %% where we write $(q, \val{}{}) \models \Phi$ iff $\Phi(q,
+  %% \val{}{}) = \true$.
+  A property $\Phi$ is \emph{initial} if
+  $s^0_{\semopen{B}} \models \Phi$.
+  %% \todoSB{Do we need this?}\hl{;
+  %% it is \emph{reachable} iff there exists a possibly empty path
+  %% $s^0_{\semopen{B}} \goesto{a^1, \val{1}{}} s^1 \goesto{a^2,
+  %%   \val{2}{}} \cdots \goesto{a^n, \val{n}{}} s^n$, such that
+  %% $s^n \models \Phi$}.
+\end{definition}
+
+\label{property:reset}
+\addSB{Although we define properties as state predicates, any
+  appropriate logic can be used to specify them.  For instance, the
+  property \emph{``There is always a possibility to reset the system
+    or resume operation after a single failure'' (\ie without
+    additional failures occuring in the meantime)} enforced by the
+  Failure Monitor architecture can be specified using CTL as $\AG
+  \bigl(\PortFail \rightarrow \EU[]{\lnot \PortFail}{(\PortResume \lor
+    \PortReset)}\bigr)$.  Additional properties are provided in
+  \app{properties}.}
+
+%% \todoSB{Cite the original paper somewhere.}
+The main idea of our approach is that an architecture enforces
+its characteristic property on the set of its operand components.
+From this point of view, the set of coordinating components is
+not relevant, neither are their states.  Thus, to talk about
+properties enforced by architectures, we consider properties on
+the unrestricted composition of the operand components as
+formalized by the following definition.
+
+\begin{definition}[Enforcing properties]
+  \label{defn:enforce}
+  Let $A = \tuple{\cC, P_A, V_A, \export[A], \Gamma}$ be an architecture; let $\cB$
+  be a set of components and $\Phi$ an initial property of
+  their parallel composition $\Gamma_{\|}(\cB)$,
+  with $\Gamma_{\|} = \setdef{(a,\true,\emptyset)}{a \subseteq \bigcup_{B \in \cB} P_B}$.
+  We say that \emph{$A$ enforces $\Phi$ on
+    $\cB$} iff, for every state $s = (s_c, s_b)$ reachable in
+  $\semopen{A(\cB)}$, with 
+  $s_c \in \prod_{C \in \cC} S_{\semopen{C}}$ and
+  $s_b \in \prod_{B \in \cB} S_{\semopen{B}}$,
+  we have $s_b \models \Phi$.
+\end{definition}
+
+According to the above definition, when we say that an
+architecture enforces some property $\Phi$, it is implicitly
+assumed that $\Phi$ is initial for the coordinated components.
+Below, we omit mentioning this explicitly.
+
+\defn{up:compat} in \secn{arch:appendix} provides a formal definition
+of the notion of \emph{upwards compatibility}, which we present here
+informally due to page limitations.  Two architectures $A_1$ and $A_2$
+are said to be upwards compatible iff, whenever their composition
+involves the fusion of two interactions $a_1 = a \cap P_{A_1}$ and
+$a_2 = a \cap P_{A_2}$ (see \eq{arch:composition}), whereof one, say
+$a_1$, is inhibited in a given state by a larger interaction $b_1
+\supset a_1$, there exists an interaction $b_2 \supseteq a_2$ that can
+be fused with $b_1$ to form an interaction enabled in the same state.
+
+\begin{theorem}[Preserving enforced properties]
+  \label{thm:combining}
+  Let $\cB$ be a set of components; let $A_i = \tuple{\cC_i, V_{A_i},
+  P_{A_i}, \export[A_i], \Gamma_i}$, for $i = 1,2$, be two upwards compatible architectures
+  enforcing on $\cB$ the properties $\Phi_1$ and $\Phi_2$
+  respectively.  The composition $A_1 \arcomp A_2$ enforces on
+  $\cB$ the property $\Phi_1 \land \Phi_2$.
+\end{theorem}
+
+%****************************************************************
+
+%****************************************************************
 
@@
 \bibliographystyle{abbrv}
-\bibliography{biblio}
+\bibliography{biblio,biblioFromPnets}
 
@@
 operation.} to remove the
-\emph{input marker} of variables. Formally:
+\emph{input marker} of variables\footnote{$\overline{S}$ denotes a set of $S$.}. Formally:
 \[

### 2019-02-01 2016-Weak-FH-Bisim/WeakBisim.tex
correction Lemma 5

@@
 where for all $l\in L$:\\
-$
-s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
-$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i}}}
-\\
-\Pred=\bigwedge_{i=0}^{m_1}\Pred^1_i\land\Pred\,^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land (\bigwedge_{i=0}^{m_2}\Pred\,^3_i\subst{\Post^2})\bigotimes_{i=0}^{m_1}\subst{\Post^1_i}\\
-\Post=(\bigotimes_{i=0}^{m_2}\Post^3_i)\subst{\Post^2}\bigotimes_{i=0}^{m_1}\subst{\Post^1_i}
+$s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
+$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i}}}\\
+\Pred=\bigwedge_{i=0}^{m_1}\big(\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land \bigwedge_{i=0}^{m_2}\Pred_i^3\big(\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}(\subst{\Post^2}  \bigotimes_{j=0}^{i-1}\subst{\Post^3_i})\big)\\
+\Post=\bigotimes_{i=0}^{m_2}\Post^3_i\big(\subst{\Post^2}\bigotimes_{i=0}^{m_1}\subst{\Post^1_i}\big)
 $\\
+
 We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$:
@@
 				(\beta^1_{pj})^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
-				{\Pred^1_p}\!',  
-				{\Post^1_p}\!'}
+				{(\Pred^1_p)}',  
+				{(\Post^1_p)}'}
 			{\ostate{s_{p l}^{l\in L\setminus L_Q}} \OTarrow {\tau}
@@
 			{
-				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred^1_p}\!''},  
-				{{\Post^1_p}\!''}}
+				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{(\Pred^1_p)}''},  
+				{{(\Post^1_p)}''}}
 				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
@@
 $
-\TODO{from here simplify the double indices in beta and gamma}
-such that  $\Pred^1_p \iff {\Pred^1_p}\!'
-		\land {\Pred^1_p}\!''\land \alpha_p=\beta_{pj_0}$, $\Post^1_p={\Post^1_p}\!'\uplus 
-		{\Post^1_p}\!''$ where ${{\Post^1_p}\!''}$ is the restriction of $\Post^1_p$ over variables of $\Leaves(Q)$.\\
+such that  $\Pred^1_p \iff {(\Pred^1_p)}'
+		\land {(\Pred^1_p)}''\land \alpha_p=\beta_{pj_0}$, $\Post^1_p={(\Post^1_p)}'\uplus 
+		{(\Post^1_p)}''$ where ${{(\Post^1_p)}''}$ is the restriction of $\Post^1_p$ over variables of $\Leaves(Q)$.\\
 Else $Q$ does not move and we have: \\
@@
 			{
-				(\beta^1_{p})_j^{j\in (J\setminus \Holes(Q)) }, 
-				{\Pred^1_p}\!',  
-				{\Post^1_p}\!'}
+				(\beta^1_{pj})^{j\in (J\setminus \Holes(Q)) }, 
+				{(\Pred^1_p)}',  
+				{(\Post^1_p)}'}
 			{\ostate{(s_{p l})^{l\in L\setminus L_Q}} \OTarrow {\tau}
@@
 			{
-				(\beta^2)_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
+				(\beta^2_j)^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
 				{\Pred^2}',  
@@
 			{
-				(\beta^2)_j^{j\in J\cap\Holes(Q)}, {\Pred^2}'',  
+				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {\Pred^2}'',  
 				{\Post^2}''}
@@
 where for all $l\in L$:\\
-\TODO{a reprendere avec la nouvelle decomp ; add the v of visible}
-
 $s_l=s_{0l} \wedge s_{{(m_1+1)}l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)}l=s'_l$\\
@@
 			{
-				(\beta^1_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred^1_p}''},  
+				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred^1_p}''},  
 				{{\Post^1_p}''}}
@@
 			{
-				(\beta^3_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred^3_p}''},  
+				(\beta^3_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred^3_p}''},  
 				{{\Post^3_p}''}}
@@
 			{
-				(\beta_{p})_j^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
+				(\beta_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
 				{{\Post_p}\!\!''}}
@@
 			{
-				(\beta^2)_j^{j\in J\cap\Holes(Q)}, {{\Pred^2}''},  
+				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred^2}''},  
 				{{\Post^2}''}}
@@
 $\\ 
-\TODO{ Attention peut dire que ${{\Pred^1_p}''}, {{\Pred^2}''}$ are diffrent from previous one}\\ 
-Thereafter, by Lemma \ref{lem-rel-OT-WOT} we obtain the following weak open transition:
+Thereafter, by Lemma \ref{lem-rel-OT-WOT} we can deduce the following weak open transition:
 \begin{mathpar}
@@
 			{
-			(\gamma_k)_j^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
+			(\gamma_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
 				{{\Post_k}}}
@@
 \end{mathpar}
-$\forall l. v_l=v_{0l} \wedge v_l'=v_{n_kl}$\\
-$\forall j \in {j\in (J\cap\Holes(Q))},\quad
-\displaystyle{\gamma_{kj} }=\mybigdotcup_{i=0}^{(n'_1-1)}\!\!(\beta^1_{ij})\,\dotcup\,(\set{\beta^2})_j\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(len-1)}\!\!\!(\beta^3_{ij})
+$\forall l \in L_Q. v_l=v_{0l} \wedge v_l'=v_{n_kl}$\\
+$\forall j \in {j\in (J\cap\Holes(Q))},\,
+\displaystyle{\gamma_{kj} }=\mybigdotcup_{i=0}^{(n'-1)}\!\!\vis{\beta^1_{ij}}\,\dotcup\,\vis{\set{\beta^2_j}}\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij}}
 \\
-\Pred_k=\!\!\bigwedge_{i=0}^{(n'_1-1)}\!\!
-{\Pred_i^1}''\land{\Pred^2}''\bigotimes_{i=0}^{(n'_1-1)}\subst{{\Post_i^1}''}\land \big(\!\!\!\!\!\bigwedge_{i=(n'+1)}^{(len-1)}\!\!{\Pred^3_i}''\subst{{\Post^2}''}\big)\bigotimes_{i=0}^{(n'_1-1)}\subst{{\Post^1_i}''}\\
-\Post_k=\big(\!\!\!\!\bigotimes_{i=(n'+1)}^{(len-1)}{\Post^3_i}''\big)\subst{{\Post^2}''}\bigotimes_{i=0}^{(n'_1-1)}\subst{{\Post^1_i}''}
+\Pred_k=\big(\!\!\!\bigwedge_{i=0}^{(n'-1)}\!\!
+{\Pred_i^1}''\bigotimes_{j=0}^{(i-1)}\subst{{\Post_j^1}''}\big)
+\land{\Pred^2}''\bigotimes_{i=0}^{(n'-1)}\subst{{\Post_i^1}''}\land\\
+\mbox{~~~~~~~~~~~~~~~~~~~~~~~~~~~~}\Big(\!\!\!\bigwedge_{i=(n'+1)}^{(n_k-1)}\!\!\!{\Pred^3_i}''\bigotimes_{i=0}^{(n'-1)}\subst{{\Post^1_i}''}\subst{{\Post^2}''}\Big)\bigotimes_{j=0}^{(i-1)}\subst{{\Post^3_j}''}\\
+\Post_k=\Big(\!\!\!\!\bigotimes_{i=(n'+1)}^{(n_k-1)}{\Post^3_i}''\subst{{\Post^2}''}\bigotimes_{i=0}^{(n'-1)}\subst{{\Post^1_i}''}\Big)
 $\\
@@
 \TODO{link gamma j 0 with the alpha k ; this ises the visible abstraction and the ewautaions of 1,2,3 decomposition}
+
+From cases 1, 2 and 3 we have for all $k\in [0\ldots n]$, $\beta_{kj_0}=\alpha_k$.
+Moreover, we have: $\displaystyle{\gamma_{kj_0} }=\mybigdotcup_{i=0}^{(n'-1)}\!\!\vis{\beta^1_{ij_0}}\,\dotcup\,\vis{\set{\beta^2_{j_0}}}\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij_0}}$ \TODO{?????}\\
+
 For  $\gamma_{j_0}=[\beta_0..\beta_n]$ we have $n$ weak open transitions  $\symb{WOT}_k$ such that $k\in [0\ldots n]$.

### 2019-02-01 2018-Arch-pNets/arch-pNets.tex
skype changes and shorter 2.1

@@
 and $\variables$ a set of \emph{variables}. Within $\Talg$, we distinguish a set of
-\emph{data expressions} $\exprs{\variables}$; $e_i$ ranges over boolean expressions, and a set of \emph{Boolean
+\emph{data expressions} $\exprs{\variables}$, $e$ ranges over  expressions; and a set of \emph{Boolean
 expressions} 
@@
 $\actions{\variables}$, with $\actions{\variables}\subseteq\Talg$.
-We  use
-\[
-\assigns{\variables} \bydef{=}
-\Setdef{(x_i := e_i)^{i \in I}}{
-  x_i^{i \in I}\subseteq \variables,
-  e_i^{i \in I}\subseteq \exprs{\variables},
-  I \text{ is a finite index set}
-}
-\]
-to denote the set of \emph{variable assignments}.  $u$ ranges over sets of assignments.
-To be able to reason about the data flow between actions, we
-distinguish \emph{input variables} of the form $?x$ within terms; the function
-$\vars(t)$ identifies the set of variables in a term
-$t\in\Talg$, and $iv(t)$ returns its input variables.
+We define $\assigns{\variables}$ as the set of variable assignments of the form: $(x_i := e_i)^{i \in I}$. 
+%\[
+%\assigns{\variables} \bydef{=}
+%\Setdef{(x_i := e_i)^{i \in I}}{
+%  x_i^{i \in I}\subseteq \variables,
+%  e_i^{i \in I}\subseteq \exprs{\variables},
+%  I \text{ is a finite index set}
+%}
+%\]
+%to denote the set of \emph{variable assignments}. 
+ $u$ ranges over sets of assignments.
+%To be able to reason about the data flow between actions, we
+%distinguish \emph{input variables} of the form $?x$ within terms; t
+The function
+$\vars(t)$ identifies the set of variables in a term.
+%$t\in\Talg$, and $iv(t)$ returns its input variables.
 
@@
 %on the finite branching of the transition relation.
+We need to introduce input variables to reason about the data flow between actions.
 We  define the set of actions a pLTS can use ($a$
 ranges over action labels):\\
-%. Action terms are  of the form 
+% Action terms are  of the form 
 $\alpha=a(?x_i^{i \in I}, 
@@
 O}{two coordinators and four dangling ports, which can be grouped into two holes (see \secn{encoding} below).
-Disregarding the maximal progress priority, o}ne of its possible open-transitions is:\\[-2ex]
+Disregarding the maximal progress priority, o}ne of its possible open-transitions is:\\[-2ex] \noteLH{maximal progress undefined}
 %%   \footnote{Note the underlined action notation that we use to represent synchronised actions, i.e.

### 2019-02-01 2018-Arch-pNets/arch-pNets.tex
formula ?
Shorter pnets and ot

@@
 
-\paragraph{pNets definition.}
-\label{section:pNets}
+%\paragraph{Definitions.}
+%\label{section:pNets}
 A pLTS is a labelled transition system with variables that can be
@@
   $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
-  J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
-$\alpha'_k$. The Boolean expression $g_k $, such that $\vars(g_k)\subseteq \bigcup_{l\in 
-I_k\uplus J_k}{\vars({\alpha_l})}$, is a guard associated to the vector.
+  J_k}{\vars({\alpha_l})}$. The global action  is
+$\alpha'_k$,  $g_k$ is a guard associated to the vector.
 
@@
 %\item
-The set of \emph{holes} $\Holes(\pNet_{i_1})$ of a pNet is the indexes of the holes of the pNet 
+The set of \emph{holes} $\Holes(\pNet)$ of a pNet is the indexes of the holes of the pNet 
 itself plus the indexes of all the holes of its subnets (we suppose those indexes 
@@
 
-\paragraph{Operational Semantics for Open pNets.}
-\label{section:op-semantics}
-
-\noteLH{a pred is a g a post is a u (modified macros!)}
+%\paragraph{Operational Semantics.}
+%\label{section:op-semantics}
 \renewcommand{\Pred}{g}
 \renewcommand{\Post}{u}
-The semantics of an open pNets is expressed as an open automaton, i.e., an automaton where each transition composes the actions of several holes, 
-the transition occurs if some predicates hold, and can involve a 
+The semantics of an open pNets is expressed as  an automaton where each transition composes the actions of several holes, 
+the transition occurs if some predicates hold, and can involve  
  state modifications.
@@
   \label{Example:TimerOT3}
-  The \texttt{Failure TimerMonitor} pNet of \Fig{FailureTimer:pNet} has \replaceSB{2 controllers 
-  and 2 holes.
-O}{two coordinators and four dangling ports, which can be grouped into two holes (see \secn{encoding} below).
-Disregarding the maximal progress priority, o}ne of its possible open-transitions is:\\[-2ex] \noteLH{maximal progress undefined}
-%%   \footnote{Note the underlined action notation that we use to represent synchronised actions, i.e.
-actions that are the result of a synchronisation and that we declare as \emph{non-observable}.
-Those actions are only used for monitoring purposes and statement of properties but cannot be synchronised again in a synchronisation vector.
-This allows us to define a weak bisimilarity equivalence with p=compositional properties.}
-%%   : 
-%% \noteLH{underline notation might be a bit too much for this paper : see at the end if we remove it or not (will we use it?)}
-% \smallskip
-%$  OT_1  = \openrule
-%{\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
-%{\ostate{00} \OTarrow{\underline{\alpha_4}} \ostate{11}}
-%$
-%\medskip
+We now briefly illustrate an open transition:
 \begin{small}\[ \openrule
-  {\{B\mapsto fail(b0)\},\\
-    t<GetMax(z) \land b1=true \land b1=>b0 \land z'= (z \cap (b1?zone;TopInt)+t) {\color{blue}\land (t' = t) \land (zone' = zone)},\\
-    \{z:=z', {\color{blue}t := t'+1, zone := zone'}\} }
-  {\ostate{11} \OTarrow{\alpha_0} \ostate{12}}
+  {\{B\mapsto fail(b)\},
+    t<Max \land b=true ,
+    \{t' := t+1\} }
+  {\ostate{11} \OTarrow{\alpha(t)} \ostate{12}}\vspace{-1.5ex}
   \]
-\end{small}\vspace{-1.5ex}
+\end{small}
 %
@@
 %global action is denoted $\alpha_4$.
-
-It corresponds to the firing of the \replaceSB{connector
-$''tick, fail, fail''$}{interaction $\listset{\NameTimer.\PortTick, \PortFail, \NameCtrl.\PortFail}$}.
+It requires the hole at label $B$ to fire a $fail(b)$ action, with the condition $b=true$ and the state variable $t<Max$.
+In this case, the global pNet goes from state $\ostate{11}$ to state $\ostate{12}$ where $t'=t+1$.
+This emits a global action $\alpha(t)$.
+%
+%It corresponds to the firing of the \replaceSB{connector
+%$''tick, fail, fail''$}{interaction $\listset{\NameTimer.\PortTick, \PortFail, \NameCtrl.\PortFail}$}.
 It states that, if the hole $B$ performs an action $fail$, and the (complex) guard is satisfied, then the variable $z$ is set to $z1$ (as specified by the guard), then the transition below the dotted line occurs and a global action labelled $\alpha_0$ occurs.
 Only the second pLTS performs a transition from state $1$ to state $2$.
-The guard corresponds both to the guard of this transition and to synchronisation vector constraints.
+%The guard corresponds both to the guard of this transition and to synchronisation vector constraints.
 \end{example}

### 2019-02-01 2018-Arch-pNets/arch-pNets.tex
skype notes and notations
added some max progress results

--- 2019-02-01 2018-Arch-pNets/arch-pNets.tex
@@
 
+  \noteIn{Checking this on the resulting open automaton should be understood after application of the encoding, namely here the original ``fail'' event must be an effective ``fail'' of the hole ``B'', that is a ``fail(true)'' action in the automaton.}
+
 \item As long as no failure has occured, the $z$ variable of the
@@
 - Transition: t1---timeout-->t1, [t in z], { t := (t+1)}
-- Variable: t, State: t1, Value(s) = 0,0,(t+1),
-- Variable: z, State: t1, Value(s) = TopInt,z1,
 pLTS: Failure
@@
 - Transition: s3---reset-->s1, {}
-- Variable: zone, State: s1, Value(s) = minZone,maxZone,
 Holes: B
@@
     OT2 ------------------------------------------------------------
-        <t1_s1>-----fail----><t1_s1>
+        <t1_s1>-----fail(b0:sva_SV0:1:1)----><t1_s1>
 
@@
     OT3 ------------------------------------------------------------
-        <t1_s1>-----fail----><t1_s2>
+        <t1_s1>-----fail(true)----><t1_s2>
 
@@
     OT6 ------------------------------------------------------------
-        <t1_s2>-----fail----><t1_s2>
+        <t1_s2>-----fail(b0:sva_SV0:1:1)----><t1_s2>
 
@@
     OT10 ------------------------------------------------------------
-        <t1_s3>-----fail----><t1_s3>
+        <t1_s3>-----fail(b0:sva_SV0:1:1)----><t1_s3>
 
@@
 
+  Now the version with the Max Progress encoding.
+ This modifies both the pLTS transitions, and the synchronisation vectors:
+
+\small\begin{verbatim}
+FailureTimerArchi
+--------------------
+SV0 SVs: <tick(z, t, z1), fail(zone, b1), fail(b0), _>-->alpha0,
+                          [((b1->b0)/\(z1=z/\(((b1?(zone)TopInt)))+t)))]
+SV1 SVs: <cancel(b1), resume(b2), resume, _>-->alpha1, (b1=b2)
+SV2 SVs: <timeout, timeout, _, ask>-->alpha2
+SV3 SVs: <_, reset, _, reset>-->alpha3
+SV4 SVs: <init, init, _, _>-->alpha4
+pLTS: Timer
+- Transition: t0---init-->t1, { t := 0 z := TopInt}
+- Transition: t1---tick(z, t, z1)-->t1, [(t<GET_MAX z)], { t := (t+1) z := z1}
+- Transition: t1---cancel(false)-->t1, {}
+- Transition: t1---cancel(true)-->t1, { t := 0 z := TopInt}
+- Transition: t1---timeout-->t1, [t in z], { t := (t+1)}
+pLTS: Failure
+- Transition: s0---init-->s1, { zone := minZone,maxZone}
+- Transition: s1---timeout-->s1, {}
+- Transition: s1---resume(false)-->s1, {}
+- Transition: s1---fail(zone, false)-->s1, {}
+- Transition: s1---fail(zone, true)-->s2, {}
+- Transition: s2---fail(zone, false)-->s2, {}
+- Transition: s2---resume(false)-->s2, {}
+- Transition: s2---resume(true)-->s1, {}
+- Transition: s2---timeout-->s3, {}
+- Transition: s3---fail(zone, false)-->s3, {}
+- Transition: s3---resume(false)-->s3, {}
+- Transition: s3---reset-->s1, {}
+Holes: B
+Holes: E
+\end{verbatim}
+
+  The new (simplied) OA is in figure \ref{schema:ArchFailure:OA-MaxProgress}.
+  Here we give the detail only of the modifed OTs:
+
+  \begin{figure}[t]
+  \centering
+  \includegraphics[width=\columnwidth]{TimerOAMaxProgress}
+  \caption{The open Automaton of the Failure Monitor Architecture}
+  \label{schema:ArchFailure:OA-MaxProgress}
+\end{figure}
+
+\begin{itemize}
+\item OT:2 has changed because $b0=true$ is no longer possible
+\item OT7 has disappeared because it is now unsat.
+\end{itemize}
+
+\small\begin{verbatim}
+	    {t1---tick(z, t, z1)-->t1, s1---fail(zone, true, false)-->s1},
+            {B|->fail(b0:sva_SV0:1:1)},
+            [(t<(GET_MAX z))/\((tick(z, t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
+              /\((fail(zone, true, false))=(fail(zone:sva_SV0:1:1, bf:sva_SV0:1:1, b1:sva_SV0:1:1)))
+              /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
+              /\((bf:sva_SV0:1:1/\b0:sva_SV0:1:1)=>b1:sva_SV0:1:1)
+              /\(z1:sva_SV0:1:1=(z:sva_SV0:1:1 |Intersection| ((b1:sva_SV0:1:1?(zone:sva_SV0:1:1):(TopInt))+t:sva_SV0:1:1)))],
+            {t := t+1, z := z1}
+	OT:2 ------------------------------------------------------------
+		<t1_s1>-----fail(false)----><t1_s1>
+
+\end{verbatim}
+
 \end{document}

### 2019-02-01 2016-Weak-FH-Bisim/WeakBisim.tex
correction

@@
 $\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i}}}\\
-\Pred=\bigwedge_{i=0}^{m_1}\big(\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land \bigwedge_{i=0}^{m_2}\Pred_i^3\big(\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}(\subst{\Post^2}  \bigotimes_{j=0}^{i-1}\subst{\Post^3_i})\big)\\
-\Post=\bigotimes_{i=0}^{m_2}\Post^3_i\big(\subst{\Post^2}\bigotimes_{i=0}^{m_1}\subst{\Post^1_i}\big)
+\Pred=\bigwedge_{i=0}^{m_1}\big(\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land \bigwedge_{i=0}^{m_2}\Pred_i^3\big((\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1})\big)\\
+\Post=\bigotimes_{i=0}^{m_2}\Post^3_i\big(\subst{\Post^2}\bigotimes_{j=0}^{m_1}\subst{\Post^1_j}\big)
 $\\
@@
 $s_l=s_{0l} \wedge s_{{(m_1+1)}l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)}l=s'_l$\\
-$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\},\quad
-\displaystyle{\gamma_j}=\mybigdotcup_{i=0}^{m_1}  (\beta^1_{ij}) \dotcup  (\set{\beta^2}_i) \dotcup \mybigdotcup_{i=0}^{m_2} (\beta^3_{ij})
+$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\},
+\displaystyle{\gamma_j}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{ij}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{ij}}
 \\
 \Pred\,'=\bigwedge_{i=0}^{m_1}
-({\Pred_i^1}'\bigotimes_{i=0}^{i-1}\subst{{\Post_i^1}'})
-\land{\Pred^2}'\bigotimes_{i=0}^{m_1}\subst{{\Post_i^1}'}\land (\bigwedge_{i=0}^{m_2}{\Pred\,^3_i}'(\bigotimes_{i=0}^{m_1}\subst{{\Post^1_i}'})\subst{{\Post^2}'}(\bigotimes_{j=0}^{i-1}\subst{{\Post^3_j}'}))\\
-\Post'=(\bigotimes_{i=0}^{m_2}{\Post^3_i}')\subst{{\Post^2}'}\bigotimes_{i=0}^{m_1}\subst{{\Post^1_i}'}
+({\Pred_i^1}'\bigotimes_{j=0}^{i-1}\subst{{\Post_j^1}'})
+\land{\Pred^2}'\bigotimes_{i=0}^{m_1}\subst{{\Post_i^1}'}\land 
+(\bigwedge_{i=0}^{m_2}{\Pred\,^3_i}'(\bigotimes_{j=0}^{i-1}\subst{{\Post^3_j}'})\subst{{\Post^2}'}(\bigotimes_{j=0}^{m_1}\subst{{\Post^1_j}'}))\\
+\Post'=(\bigotimes_{i=0}^{m_2}{\Post^3_i}')\subst{{\Post^2}'}\bigotimes_{j=0}^{m_1}\subst{{\Post^1_j}'}
 $
@@
 By considering $\tau$  actions we split the sequence of actions into $n$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.
-We can decompose each of the $n$ subsequences, where sequence  $k$ has length $n_k$,  as follows:\\
+We can decompose each of the $n$ subsequences; the length of the subsequence number $k$ is $n_k$,  and the subsequence is made of the following OTs:\\
 $\forall p \in [0\ldots (n'-1)] Q\models{\openrule
@@
 			{
-			(\gamma_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
+			(\gamma'_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
 				{{\Post_k}}}
-			{\ostate{v_{l}^{l\in L_Q}} \OTWeakarrow {\alpha_{k}}
+			{\ostate{v_{l}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
 				\ostate{v_{l}'^{l\in L_Q}}}
@@
 $\forall l \in L_Q. v_l=v_{0l} \wedge v_l'=v_{n_kl}$\\
-$\forall j \in {j\in (J\cap\Holes(Q))},\,
-\displaystyle{\gamma_{kj} }=\mybigdotcup_{i=0}^{(n'-1)}\!\!\vis{\beta^1_{ij}}\,\dotcup\,\vis{\set{\beta^2_j}}\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij}}
+$\forall j \in  (J\cap\Holes(Q)),\,
+\displaystyle{\gamma'_{kj} }=\mybigdotcup_{i=0}^{(n'-1)}\!\!\vis{\beta^1_{ij}}\,\dotcup\,\vis{\set{\beta^2_j}}\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij}}
 \\
@@
 \land{\Pred^2}''\bigotimes_{i=0}^{(n'-1)}\subst{{\Post_i^1}''}\land\\
-\mbox{~~~~~~~~~~~~~~~~~~~~~~~~~~~~}\Big(\!\!\!\bigwedge_{i=(n'+1)}^{(n_k-1)}\!\!\!{\Pred^3_i}''\bigotimes_{i=0}^{(n'-1)}\subst{{\Post^1_i}''}\subst{{\Post^2}''}\Big)\bigotimes_{j=0}^{(i-1)}\subst{{\Post^3_j}''}\\
+~\qquad\qquad\qquad\Big(\!\!\!\bigwedge_{i=(n'+1)}^{(n_k-1)}\!\!\!{\Pred^3_i}''\bigotimes_{j=n'+1}^{(i-1)}\subst{{\Post^3_j}''}\subst{{\Post^2}''}\bigotimes_{i=0}^{(n'-1)}\subst{{\Post^1_i}''}\Big)\\
 \Post_k=\Big(\!\!\!\!\bigotimes_{i=(n'+1)}^{(n_k-1)}{\Post^3_i}''\subst{{\Post^2}''}\bigotimes_{i=0}^{(n'-1)}\subst{{\Post^1_i}''}\Big)
@@
 
-From cases 1, 2 and 3 we have for all $k\in [0\ldots n]$, $\beta_{kj_0}=\alpha_k$.
-Moreover, we have: $\displaystyle{\gamma_{kj_0} }=\mybigdotcup_{i=0}^{(n'-1)}\!\!\vis{\beta^1_{ij_0}}\,\dotcup\,\vis{\set{\beta^2_{j_0}}}\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij_0}}$ \TODO{?????}\\
+From cases 1, 2 and 3 we have for all $k\in [0\ldots n]$, $\beta_{kj_0}=\alpha_k$. Moreover, we have:\\ 
+$\displaystyle{\gamma_{j_0}}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{i{j_0}}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{i{j_0}}}=(\alpha'_k)^{k\in 1..n}=\{\alpha_p|p\in [0..m_1+m_2+1] \land \alpha_p\neq \tau\}$
+%$\displaystyle{\gamma_{kj_0} }=\mybigdotcup_{i=0}^{(n'-1)}\!\!\vis{\beta^1_{ij_0}}\,\dotcup\,\vis{\set{\beta^2_{j_0}}}\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij_0}}$ \TODO{?????}\\
 

### 2019-02-01 2018-Arch-pNets/arch-pNets.tex

@@
   \label{Example:TimerOT3}
-  The \texttt{Failure TimerMonitor} pNet of \Fig{FailureTimer:pNet} has \replaceSB{2 controllers 
-  and 2 holes.
-O}{two coordinators and four dangling ports, which can be grouped into two holes (see \secn{encoding} below).
-Disregarding the maximal progress priority, o}ne of its possible open-transitions is:\\[-2ex] \noteLH{maximal progress undefined}
-%%   \footnote{Note the underlined action notation that we use to represent synchronised actions, i.e.
-actions that are the result of a synchronisation and that we declare as \emph{non-observable}.
-Those actions are only used for monitoring purposes and statement of properties but cannot be synchronised again in a synchronisation vector.
-This allows us to define a weak bisimilarity equivalence with p=compositional properties.}
-%%   : 
-%% \noteLH{underline notation might be a bit too much for this paper : see at the end if we remove it or not (will we use it?)}
-% \smallskip
-%$  OT_1  = \openrule
-%{\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
-%{\ostate{00} \OTarrow{\underline{\alpha_4}} \ostate{11}}
-%$
-%\medskip
+We now briefly illustrate an open transition:
 \begin{small}\[ \openrule
-  {\{B\mapsto fail(b0)\},\\
-    t<GetMax(z) \land b1=true \land b1=>b0 \land z'= (z \cap (b1?zone;TopInt)+t) {\color{blue}\land (t' = t) \land (zone' = zone)},\\
-    \{z:=z', {\color{blue}t := t'+1, zone := zone'}\} }
-  {\ostate{11} \OTarrow{\alpha_0} \ostate{12}}
+  {\{B\mapsto fail(b)\},
+    t<Max \land b=true ,
+    \{t' := t+1\} }
+  {\ostate{11} \OTarrow{\alpha(t)} \ostate{12}}\vspace{-1.3ex}
   \]
-\end{small}\vspace{-1.5ex}
+\end{small}
 %

### 2019-02-01 2018-Arch-pNets/arch-pNets.tex
abstract et keyword

@@
 \begin{abstract}
-  We extend the theory of architectures with a general
-  mechanism for handling various types of data transfer.  We
-  encode this extended model into the open pNet semantic
-  model and show how this encoding can be used to verify
-  that an architecture does, indeed, enforce its
-  characteristic property.
-
-\keywords{}
+This paper provides a solution for the compositional design of systems and their verification.
+The approach taken consists in designing architectural elements that guaranty safety properties and composing them to build a safe system.
+
+More precisely, this article provides a theory of architectures based on the BIP system.
+It extends preliminary work in this domain by handling data: definition of data-domains,  operations on  data-domains, and data transfer.
+These architectures and the safety properties they ensure can be composed.
+We then illustrate how to verify the properties of the architectures in an SMT solver; this is relying on an encoding into an intermediate model called pNets that already supports SMT-based verification.
+Additionally, the translation into  the open pNet semantic
+  model gives us a strong insight on the  coordination mechanisms existing in the two models and their comparison. The approach is illustrated by a case-study where key safety properties are verified.
+
+\keywords{Parametrised verification, composition, safety, interaction models.}
 \end{abstract}

### 2019-02-07 2018-Arch-pNets/arch-pNets.tex
Updated title and abstract

--- 2019-02-01 2018-Arch-pNets/arch-pNets.tex
@@
 
-\title{BIP Architectures and Open pNets}
+\title{Verification of concurrent design patterns with data}
 
@@
 Eric~Madelaine\inst{3}
-\and
-...
 }
@@
 \begin{abstract}
-  We extend the theory of architectures with a general
-  mechanism for handling various types of data transfer.  We
-  encode this extended model into the open pNet semantic
-  model and show how this encoding can be used to verify
-  that an architecture does, indeed, enforce its
-  characteristic property.
-
-\keywords{}
+We provide a solution for the design of safe concurrent systems by
+compositional application of verified design patterns\mdash which we
+call \emph{architectures}\mdash to a minimal set of functional
+components.  To this end, we extend the theory of architectures
+developed previously for the BIP framework with the elements necessary
+for handling data: definition and operations on data domains, syntax
+and semantics of composition operators involving data transfer.  Under
+monotonicity assumptions on guards and assignments, composition of
+architectures preserves their characteristic safety properties.
+
+To verify that individual architectures do enforce their associated
+properties, we provide a non-trivial encoding into an intermediate
+model called open pNets that supports SMT-based verification.
+Additionally, the translation into the open pNet semantic model gives
+us a strong insight and a comparison of the coordination mechanisms
+provided by the two frameworks.  The approach is illustrated by a case
+study based on a previously developed BIP model of a nanosatellite
+on-board software.
+
+\keywords{Parametrised verification, composition, safety, interaction
+  models.}
 \end{abstract}

### 2019-02-07 2018-Arch-pNets/arch-pNets.tex
SMT section, et nouveaux dessins

@@
 \newcommand{\todoEM}[2][color=green!40, size=\tiny]{\todo[#1]{\textbf{To-do Eric:} {#2}}}
+\newcommand{\noteEMin}[2][inline,color=green!40]{\todo[#1]{{#2}\Eric}}
 
@@
 parameters. Such open systems can be used to define composition operators or structuring architectures.
-It is possible to reason, in an SMT engine, on the symbolic automaton that represents the behaviour of a pNets with holes and that communicates value~\cite{AVOCS}.
+It is possible to reason, in an SMT engine, on the symbolic automaton that represents the behaviour of a pNets with holes and that communicates value~\cite{HMZ-FORTE2016QBMZ-AVOCS18}.
 This encding of open pNets into Z3 that is under development is the starting point of this article.
@@
 
-\begin{indent}
-  description courte et intuitive avec reference au papier d'Avocs
-\end{indent}
+In \cite{HMZ-FORTE2016QBMZ-AVOCS18}, we have described an algorithm
+and a tool that 
+computes the open automaton encoding the semantics of an open
+pNet. This tool computes open transitions from the combinations of all
+possible behaviours and synchronisation vectors of the pNet, then makes
+use of an SMT engine to check satisfiability of the open transition
+predicates, and minimize the size of the resulting automaton.
+
+The encoding into the SMT language involves the definition of the
+action and data domains and operators, and the axiomatisation of
+domain-dependant properties, to allow the SMT engine to be as precise
+as possible (even if it cannot be complete).
+
+The resulting open automaton will later be subject to (symbolic)
+model-checking and equivalence checking algorithms, themselves
+requiring automatic proof assistance. \todoEM{trop flou pour le
+  moment, mais je n'ose pas dire des trucs trop precis... meme si on a
+  deja une implem de la FH-bisim, elle n'est pas validee!}
+
+\noteEMin{Est-ce qu'on a la place de mettre un exemple de script SMT ici ?}
 
@@
   \centering
-  \includegraphics[width=0.8\columnwidth]{TimerOADetailed}
+  \includegraphics[width=0.9\columnwidth]{TimerOADetailed}
   \caption{The open Automaton of the Failure Monitor Architecture}
@@
 obtained from our pNet. For reasons of space, we have not shown the
-detail of the open transition, but only the assignement of state
-variables, and the resulting action; you can find the full details in
+detail of the open transition, but only the assignments of state
+variables, some usefull parts of the predicates, and the resulting
+action; you can find the full details in 
 Appendix \ref{secn:full-results}. As an example, $OT_3$ is the one
@@
 the maximal progress assumption here. If we do, we get the corrected
-behaviour in Fig~\ref{schema:ArchFailure:MaxProgress}. This one
-verifies all the properties listed in  \app{properties}.
+behaviour in Fig~\ref{schema:ArchFailure:OA-MaxProgress}
+(\app{full-results}), in which $OT_7$ has 
+disappeared, and $OT_2$ and $OT_{10}$ have been restricted to
+$b0=false$. This one verifies all the properties listed in
+\app{properties}.
 
@@
   The new (simplied) OA is in figure \ref{schema:ArchFailure:OA-MaxProgress}.
-  Here we give the detail only of the modifed OTs:
+  Here we give the detail only of one the modifed OTs:
 
@@
 \begin{itemize}
-\item OT:2 has changed because $b0=true$ is no longer possible
-\item OT7 has disappeared because it is now unsat.
+\item $OT_2$ and $OT_{10}$ have changed because $b0=true$ is no longer possible
+\item $OT_7$ has disappeared because it is now unsat.
 \end{itemize}

### 2019-02-12 2018-Arch-pNets/arch-pNets.tex
nouveau OA
Skype meeting

@@
 Valuations extend canonically to expressions and denote $\val{}{}(e)$ the value of $e$ under the valuation $\val{}{}$.
-\noteLH{its the following really necessary}
-\addSB{Since we consider variables to be sorted, valuations
-  applied to expressions are interpreted as partial functions
-  $\exprs{V} \rightharpoonup \data$.}
+%\noteLH{its the following really necessary}
+%\addSB{Since we consider variables to be sorted, valuations
+%  applied to expressions are interpreted as partial functions
+%  $\exprs{V} \rightharpoonup \data$.}
 For a valuation $\val{}{}$ and an assignment $(x_i := e_i)^{i \in I}$, we define:
@@
 
-\noteEMin{Est-ce qu'on a la place de mettre un exemple de script SMT ici ?}
+%\noteEMin{Est-ce qu'on a la place de mettre un exemple de script SMT ici ?}
 
@@
 %%% compositional verification
-approaches by typing interfaces/protocols
-
-infinite/parametrized model checking?
-
-theorem proving? (too much manual effort) we need an example, we could cite Coqcots and Pycots for reconfiguration
-
-SMT on an application not using component structure. is there a strong Z3 example
-
-KeY? (I would call this symbolic execution and assume-guarantee)
+approaches by typing interfaces/protocols == Simon
+
+infinite/parametrized model checking? == ERIC + Simon
+
+theorem proving? (too much manual effort) we need an example, we could cite Coqcots and Pycots for reconfiguration == LUDO
+
+SMT on an application not using component structure. is there a strong Z3 example == Eric
+
+KeY? (I would call this symbolic execution and assume-guarantee) == LUDO
 
@@
 %*********************************************************************
-
-\section{pNets additional definitions}
-\label{secn:pNets:additional}
-
-\begin{definition}[Sorts, Holes, Leaves of pNets]
-  \begin{itemize}
-  \item  \noteSB{I think this can be lightened up a bit, since the definitions are all 
-  straightforward, whereas the notation is complex.  Maybe reformulate in words and move 
-  the formal definitions in the appendix?}
- The sort of a pNet is its signature, i.e. the set of actions it can
-perform. \noteSB{Is there any chance that, by writing assignments explicitly ($x := e$), 
-we could eliminate the need to distinguish the input variables at all? That would 
-simplify things.}\hl{In the definition of sorts, we do not need to distinguish
-input variables} (that specify the dataflow within LTSs), so for
-computing LTS sorts, we use a substitution operator\footnote{$\subst{y_k\gets x_k}^{k\in 
-K}$ is the parallel substitution 
-operation.} to remove the
-\emph{input marker} of variables\footnote{$\overline{S}$ denotes a set of $S$.}. Formally:
-\[
-\begin{array}{l}
-\Sortop(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{x \gets ?x| 
-x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~g,~(x_j\!:= {e}_j)^{j\in
-    J}\rangle} s'\in \to \} \\
-\Sortop(\mylangle \overline{\pNet}\!, %\pNet_i^{i\in I}, \Sort_j^{j\in J}
-\overline{\pNet}\!,
-\overline{\symb{SV}}\myrangle)
-=\{\alpha' |\, \overline{\alpha}%\alpha_j^{j\in J_k}
-\to\alpha'\in\set{\symb{SV}}\}
-\end{array}
-\]
-
-\item
-The set of holes of a pNet is defined inductively; the sets of holes
-in a pNet node and its subnets are all disjoint:
-  \[\begin{array}{l}
-\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset \\
-\Holes(\mylangle \pNet_i^{i\in I}\!,\Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) 
-=J\uplus{\displaystyle \bigcup_{i\in 
-I}\Holes(\pNet_i)}\\
-\forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
-\forall i_1,i_2\in I.\,i_1\neq i_2\Rightarrow  
-\Holes(\pNet_{i_1})\cap\Holes(\pNet_{i_2})=\emptyset
-\end{array}\]
-\item
-The set of leaves of a pNet is the set of all pLTSs occurring in the structure, defined 
-inductively as:
-\[\begin{array}{l}
-\Leaves(\mylangle S,s_0, \to\myrangle) \!=\!\emptyset\\%\{\mylangle S,s_0, \to\myrangle\}\\
-\Leaves(\mylangle \pNet_i^{i\in I}\!,%Sort_j^{j\in J}
-\overline{\Sort}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \biguplus_{i\in 
-I}\Leaves(\pNet_i)\uplus\{i\mapsto \pNet_i|\pNet_i\pNet_i \text{ is a }\pLTS\}}
-\end{array}\]
-\end{itemize}
-\end{definition}
+%
+%\section{pNets additional definitions}
+%\label{secn:pNets:additional}
+%
+%\begin{definition}[Sorts, Holes, Leaves of pNets]
+%  \begin{itemize}
+%  \item  \noteSB{I think this can be lightened up a bit, since the definitions are all 
+%  straightforward, whereas the notation is complex.  Maybe reformulate in words and move 
+%  the formal definitions in the appendix?}
+% The sort of a pNet is its signature, i.e. the set of actions it can
+%perform. \noteSB{Is there any chance that, by writing assignments explicitly ($x := e$), 
+%we could eliminate the need to distinguish the input variables at all? That would 
+%simplify things.}\hl{In the definition of sorts, we do not need to distinguish
+%input variables} (that specify the dataflow within LTSs), so for
+%computing LTS sorts, we use a substitution operator\footnote{$\subst{y_k\gets x_k}^{k\in 
+%K}$ is the parallel substitution 
+%operation.} to remove the
+%\emph{input marker} of variables\footnote{$\overline{S}$ denotes a set of $S$.}. Formally:
+%\[
+%\begin{array}{l}
+%\Sortop(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{x \gets ?x| 
+%x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~g,~(x_j\!:= {e}_j)^{j\in
+%    J}\rangle} s'\in \to \} \\
+%\Sortop(\mylangle \overline{\pNet}\!, %\pNet_i^{i\in I}, \Sort_j^{j\in J}
+%\overline{\pNet}\!,
+%\overline{\symb{SV}}\myrangle)
+%=\{\alpha' |\, \overline{\alpha}%\alpha_j^{j\in J_k}
+%\to\alpha'\in\set{\symb{SV}}\}
+%\end{array}
+%\]
+%
+%\item
+%The set of holes of a pNet is defined inductively; the sets of holes
+%in a pNet node and its subnets are all disjoint:
+%  \[\begin{array}{l}
+%\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset \\
+%\Holes(\mylangle \pNet_i^{i\in I}\!,\Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) 
+%=J\uplus{\displaystyle \bigcup_{i\in 
+%I}\Holes(\pNet_i)}\\
+%\forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
+%\forall i_1,i_2\in I.\,i_1\neq i_2\Rightarrow  
+%\Holes(\pNet_{i_1})\cap\Holes(\pNet_{i_2})=\emptyset
+%\end{array}\]
+%\item
+%The set of leaves of a pNet is the set of all pLTSs occurring in the structure, defined 
+%inductively as:
+%\[\begin{array}{l}
+%\Leaves(\mylangle S,s_0, \to\myrangle) \!=\!\emptyset\\%\{\mylangle S,s_0, \to\myrangle\}\\
+%\Leaves(\mylangle \pNet_i^{i\in I}\!,%Sort_j^{j\in J}
+%\overline{\Sort}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \biguplus_{i\in 
+%I}\Leaves(\pNet_i)\uplus\{i\mapsto \pNet_i|\pNet_i\pNet_i \text{ is a }\pLTS\}}
+%\end{array}\]
+%\end{itemize}
+%\end{definition}
 
@@
   \includegraphics[width=\columnwidth]{TimerOAMaxProgress}
-  \caption{The open Automaton of the Failure Monitor Architecture}
+  \caption{The open Automaton of the Failure Monitor Architecture,
+    with Maximal Progress}
   \label{schema:ArchFailure:OA-MaxProgress}

### 2019-02-13 2018-Arch-pNets/arch-pNets.tex
small typo
passe sur derniere annexe

@@
 % %%%%%%%%%%%%%%%%%%%%%
+\makeatletter
+\newcommand{\verbatimfont}[1]{\renewcommand{\verbatim@font}{\ttfamily#1}}
+\makeatother
+% %%%%%%%%%%%%%%%%%%%%%
 
@@
 It is possible to reason, in an SMT engine, on the symbolic automaton that represents the behaviour of a pNets with holes and that communicates value~\cite{HMZ-FORTE2016QBMZ-AVOCS18}.
-This encding of open pNets into Z3 that is under development is the starting point of this article.
+This encoding of open pNets into Z3 that is under development is the starting point of this article.
 Our objective is to benefit from the possibility to reason on a pNet in an SMT engine in order to prove properties on BIP architectures.
@@
 
-The standard pretty-print of OTs by the tool include the transitions
-of the pLTSs (controllers). This is not a full ``proof-carrying
-code'', but it allows for a better understanding of the construction
-of each OT.
-
-We first show the pNet input, then the twelve generated OTs in their
-verbatim form.
-
-\small\begin{verbatim}
-FailureTimerArchi
---------------------
-SV0 SVs: <tick(z, t, z1), fail(zone, b1), fail(b0), _>-->alpha0,
-                          [((b1->b0)/\(z1=z/\(((b1?(zone)TopInt)))+t)))]
-SV1 SVs: <cancel(b1), resume(b2), resume, _>-->alpha1, (b1=b2)
-SV2 SVs: <timeout, timeout, _, ask>-->alpha2
-SV3 SVs: <_, reset, _, reset>-->alpha3
-SV4 SVs: <init, init, _, _>-->alpha4
+We first show the input pNet, with its 5 synchronisation vectors, and 2 controllers.
+
+\noindent
+\verbatimfont{\small}
+\begin{verbatim}
+SV0: <tick(z, t, z1), fail(zone, b1), fail(b0), _> --> fail(b0),
+         [(b1->b0)/\(z1=z |Intersection| ((b1?zone:TopInt)+t))]
+SV1: <cancel(b1), resume(b2), resume, _> --> resume, (b1=b2)
+SV2: <timeout, timeout, _, ask> --> ask
+SV3: <_, reset, _, reset> --> reset
+SV4: <init, init, _, _> --> init
 pLTS: Timer
@@
 - Transition: t1---timeout-->t1, [t in z], { t := (t+1)}
-pLTS: Failure
-- Transition: s0---init-->s1, { zone := minZone,maxZone}
-- Transition: s1---timeout-->s1, {}
-- Transition: s1---resume(false)-->s1, {}
-- Transition: s1---fail(zone, false)-->s1, {}
-- Transition: s1---fail(zone, true)-->s2, {}
-- Transition: s2---fail(zone, false)-->s2, {}
-- Transition: s2---resume(false)-->s2, {}
-- Transition: s2---resume(true)-->s1, {}
-- Transition: s2---timeout-->s3, {}
-- Transition: s3---fail(zone, false)-->s3, {}
-- Transition: s3---resume(false)-->s3, {}
-- Transition: s3---reset-->s1, {}
-Holes: B
-Holes: E
-
-       {t0---init-->t1, s0---init-->s1},   {},  [true],
-       {t := 0, z := TopInt, zone := minZone,maxZone}
-    OT1 ------------------------------------------------------------
-        <t0_s0>-----init----><t1_s1>
-
-       {t1---tick(z, t, z1)-->t1, s1---fail(zone, false)-->s1},   {---:hb_B-->},
-       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
-         /\((tick(z, t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
-         /\((fail(zone, false))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
-         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
-         /\(z1:sva_SV0:1:1=
-         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
-       {t := t+1, z := z1}
-    OT2 ------------------------------------------------------------
-        <t1_s1>-----fail(b0:sva_SV0:1:1)----><t1_s1>
-
-       {t1---tick(z, t, z1)-->t1, s1---fail(zone, true)-->s2},   {---:hb_B-->},
-       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
-         /\((tick(z,t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
-         /\((fail(zone, true))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
-         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
-         /\(z1:sva_SV0:1:1=
-         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
-       {t := t+1, z := z1}
-    OT3 ------------------------------------------------------------
-        <t1_s1>-----fail(true)----><t1_s2>
-
-       {t1---cancel(false)-->t1, s1---resume(false)-->s1},   {---:hb_B-->},
-       [(:hb_B=fail(b0:sva_SV0:1:1)
-         /\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
-         /\((resume(false))=(resume(b2:sva_SV1:1:2)))
-         /\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],   {}
-    OT4 ------------------------------------------------------------
-        <t1_s1>-----resume----><t1_s1>
-
-       {t1---timeout-->t1, s1---timeout-->s1},   {---:hb_E-->},
-       [(:hb_E=ask)/\(t in z)],   {t := t+1}
-    OT5 ------------------------------------------------------------
-        <t1_s1>-----ask----><t1_s1>
-
-       {t1---tick(z, t, z1)-->t1, s2---fail(zone, false)-->s2},   {---:hb_B-->},
-       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
-         /\((tick(z, t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
-         /\((fail(zone, false))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
-         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
-         /\(z1:sva_SV0:1:1=
-         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
-       {t := t+1, z := z1}
-    OT6 ------------------------------------------------------------
-        <t1_s2>-----fail(b0:sva_SV0:1:1)----><t1_s2>
-
-       {t1---cancel(false)-->t1, s2---resume(false)-->s2},   {---:hb_B-->},
-       [(:hb_B=resume)/\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
-         /\((resume(false))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],   {}
-    OT7 ------------------------------------------------------------
-        <t1_s2>-----resume----><t1_s2>
-
-       {t1---cancel(true)-->t1, s2---resume(true)-->s1},   {---:hb_B-->},
-       [(:hb_B=resume)/\((cancel(true))=(cancel(b1:sva_SV1:1:2)))
-         /\((resume(true))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],
-       {t := 0, z := TopInt}
-    OT8 ------------------------------------------------------------
-        <t1_s2>-----resume----><t1_s1>
-
-       {t1---timeout-->t1, s2---timeout-->s3},   {---:hb_E-->},
-       [(:hb_E=ask)/\(t in z)],   {t := t+1}
-    OT9 ------------------------------------------------------------
-        <t1_s2>-----ask----><t1_s3>
-
-       {t1---tick(z, t, z1)-->t1, s3---fail(zone, false)-->s3},   {---:hb_B-->},
-       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
-         /\((tick(z, t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
-         /\((fail(zone, false))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
-         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
-         /\(z1:sva_SV0:1:1=
-         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
-       {t := t+1, z := z1}
-    OT10 ------------------------------------------------------------
-        <t1_s3>-----fail(b0:sva_SV0:1:1)----><t1_s3>
-
-       {t1---cancel(false)-->t1, s3---resume(false)-->s3},   {---:hb_B-->},
-       [(:hb_B=resume)/\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
-         /\((resume(false))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],   {}
-    OT11 ------------------------------------------------------------
-        <t1_s3>-----resume----><t1_s3>
-
-        {s3---reset-->s1},   {---:hb_E-->},     [(:hb_E=ask)],   {}
-    OT12 ------------------------------------------------------
-        <t1_s3>-----reset----><t1_s1>
-
-INFO  BIPArchFailureTimerMax - Total: 12 SATISFIABLE OTs
-INFO  BIPArchFailureTimerMax -        235 UNSATISFIABLE OTs
-INFO  BIPArchFailureTimerMax - Total Time: 1293 ms
-\end{verbatim}
-
-OTs simplifiees a la main:
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=\columnwidth]{TimerOADetailed}
-  \caption{The open Automaton of the Failure Monitor Architecture}
-  \label{schema:ArchFailure:OA}
-\end{figure}
-
-$  OT_1  = \openrule
-{\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
-{\ostate{00} \OTarrow{init} \ostate{11}}
-$
-\medskip
-
-$  OT_2  = \openrule
-{\{B\mapsto fail(b0)\},\\
-  t<GetMax(z) \land b1=false \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),
-  \{z:=z1\} }
-{\ostate{11} \OTarrow{fail} \ostate{11}}
-$
-\medskip
-
-  $  OT_3  = \openrule
-  {\{B\mapsto fail(b0)\},\\
-    t<GetMax(z) \land b1=true \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),
-    \{z:=z1\} }
-  {\ostate{11} \OTarrow{fail} \ostate{12}}
-  $
-  \medskip
-
-  $  OT_4  = \openrule
-  {\{B\mapsto resume\},
-    b1=false \land b2=false \land b1=b2
-    \{\}  }
-  {\ostate{11} \OTarrow{resume} \ostate{11}}
-  $
-  \medskip
-
-  $  OT_5  = \openrule
-  {\{E\mapsto ask\},
-    t \in z,
-    \{t:=t+1\}  }
-  {\ostate{11} \OTarrow{ask} \ostate{11}}
-  $
-  \medskip
-
-  $  OT_6  = \openrule
-  {\{B\mapsto fail(b0)\},\\
-    t<GetMax(z) \land b1=false \land b1=>b0 \land z1=(z \cap (b1?zone;TopInt)+t),
-    \{t:=t+1, z:=z1\} }
-  {\ostate{12} \OTarrow{fail} \ostate{12}}
-  $
-  \medskip
-
-  $  OT_7  = \openrule
-  {\{B\mapsto resume\},
-    b1=false \land b2=false \land b1=b2,
-    \{\} }
-  {\ostate{12} \OTarrow{resume} \ostate{12}}
-  $
-  \medskip
-
-  $  OT_8  = \openrule
-  {\{B\mapsto resume\},
-    b1=true \land b2=true \land b1=b2, 
-    \{t:=0, z:=TopInt\} }
-  {\ostate{12} \OTarrow{resume} \ostate{11}}
-  $
-  \medskip
-
-  $  OT_9  = \openrule
-  {\{E\mapsto ask\},
-    t \in z,
-    \{t:=t+1\} }
-  {\ostate{12} \OTarrow{ask} \ostate{13}}
-  $
-  \medskip
-
-  $  OT_{10}  = \openrule
-  {\{B\mapsto fail(b0)\},\\
-    t<GetMax(z) \land b1=false \land b1=>b0 \land z1=(z \cap (b1?zone;TopInt)+t),
-    \{t:=t+1, z:=z1\} }
-  {\ostate{13} \OTarrow{fail} \ostate{13}}
-  $
-  \medskip
-
-  $  OT_{11}  = \openrule
-  {\{B\mapsto resume\},
-    b1=false \land b2=false \land b1=b2,
-    \{\} }
-  {\ostate{13} \OTarrow{resume} \ostate{13}}
-  $
-  \medskip
-
-  $  OT_{12}  = \openrule
-  {\{E\mapsto reset\},
-    true,
-    \{\} }
-  {\ostate{13} \OTarrow{reset} \ostate{11}}
-  $
-
-  Now the version with the Max Progress encoding.
- This modifies both the pLTS transitions, and the synchronisation vectors:
-
-\small\begin{verbatim}
-FailureTimerArchi
---------------------
-SV0 SVs: <tick(z, t, z1), fail(zone, b1), fail(b0), _>-->alpha0,
-                          [((b1->b0)/\(z1=z/\(((b1?(zone)TopInt)))+t)))]
-SV1 SVs: <cancel(b1), resume(b2), resume, _>-->alpha1, (b1=b2)
-SV2 SVs: <timeout, timeout, _, ask>-->alpha2
-SV3 SVs: <_, reset, _, reset>-->alpha3
-SV4 SVs: <init, init, _, _>-->alpha4
-pLTS: Timer
-- Transition: t0---init-->t1, { t := 0 z := TopInt}
-- Transition: t1---tick(z, t, z1)-->t1, [(t<GET_MAX z)], { t := (t+1) z := z1}
-- Transition: t1---cancel(false)-->t1, {}
-- Transition: t1---cancel(true)-->t1, { t := 0 z := TopInt}
-- Transition: t1---timeout-->t1, [t in z], { t := (t+1)}
-pLTS: Failure
+pLTS: Control
 - Transition: s0---init-->s1, { zone := minZone,maxZone}
@@
 
-  The new (simplied) OA is in figure \ref{schema:ArchFailure:OA-MaxProgress}.
-  Here we give the detail only of one the modifed OTs:
+Then some of the twelve generated OTs in their verbatim form. In this format
+the first element of the premisse is a list of the moves of the pLTS
+participating in the transition. This is not part of the OT, but
+provides a trace of its construction. Also, the variables occuring in
+the actions and predicate expressions have names helping to understand
+where they come from (e.g. \verb|b0:sva_SV0| in $OT2$ below).
+This is not a full ``proof-carrying
+code'', but it allows for a better understanding of the construction
+of each OT.
+
+\verbatimfont{\small}
+\begin{verbatim}
+   {t0---init-->t1, s0---init-->s1},   {},  [true],
+   {t := 0, z := TopInt, zone := minZone,maxZone}
+OT1 ------------------------------------------------------------
+    <t0_s0>-----init----><t1_s1>
+
+   {t1---tick(z, t, z1)-->t1, s1---fail(zone, false)-->s1},   {---:hb_B-->},
+   [(:hb_B=fail(b0:sva_SV0)/\(t<(GET_MAX z))
+     /\((tick(z, t, z1))=(tick(z:sva_SV0, t:sva_SV0, z1:sva_SV0)))
+     /\((fail(zone, false))=(fail(zone:sva_SV0, b1:sva_SV0)))
+     /\(b1:sva_SV0=>b0:sva_SV0)
+     /\(z1:sva_SV0=
+     (z:sva_SV0  |Intersection| ((b1:sva_SV0?(zone:sva_SV0)TopInt))+t:sva_SV0)))],
+   {t := t+1, z := z1}
+OT2 ------------------------------------------------------------
+    <t1_s1>-----fail(b0:sva_SV0)----><t1_s1>
+
+   {t1---tick(z, t, z1)-->t1, s1---fail(zone, true)-->s2},   {---:hb_B-->},
+   [(:hb_B=fail(b0:sva_SV0)/\(t<(GET_MAX z))
+     /\((tick(z,t, z1))=(tick(z:sva_SV0, t:sva_SV0, z1:sva_SV0)))
+     /\((fail(zone, true))=(fail(zone:sva_SV0, b1:sva_SV0)))
+     /\(b1:sva_SV0=>b0:sva_SV0)
+     /\(z1:sva_SV0=
+     (z:sva_SV0  |Intersection| ((b1:sva_SV0?(zone:sva_SV0)TopInt))+t:sva_SV0)))],
+   {t := t+1, z := z1}
+OT3 ------------------------------------------------------------
+    <t1_s1>-----fail(true)----><t1_s2>
+
+   {t1---cancel(false)-->t1, s1---resume(false)-->s1},   {---:hb_B-->},
+   [(:hb_B=fail(b0:sva_SV0)
+     /\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
+     /\((resume(false))=(resume(b2:sva_SV1:1:2)))
+     /\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],   {}
+OT4 ------------------------------------------------------------
+    <t1_s1>-----resume----><t1_s1>
+
+INFO  BIPArchFailureTimerMax - Total: 12 SATISFIABLE OTs
+INFO  BIPArchFailureTimerMax -        235 UNSATISFIABLE OTs
+INFO  BIPArchFailureTimerMax - Total Time: 1293 ms
+\end{verbatim}
+
+%%    {t1---timeout-->t1, s1---timeout-->s1},   {---:hb_E-->},
+%%    [(:hb_E=ask)/\(t in z)],   {t := t+1}
+%% OT5 ------------------------------------------------------------
+%%     <t1_s1>-----ask----><t1_s1>
+
+%%    {t1---tick(z, t, z1)-->t1, s2---fail(zone, false)-->s2},   {---:hb_B-->},
+%%    [(:hb_B=fail(b0:sva_SV0)/\(t<(GET_MAX z))
+%%      /\((tick(z, t, z1))=(tick(z:sva_SV0, t:sva_SV0, z1:sva_SV0)))
+%%      /\((fail(zone, false))=(fail(zone:sva_SV0, b1:sva_SV0)))
+%%      /\(b1:sva_SV0=>b0:sva_SV0)
+%%      /\(z1:sva_SV0=
+%%      (z:sva_SV0  |Intersection| ((b1:sva_SV0?(zone:sva_SV0)TopInt))+t:sva_SV0)))],
+%%    {t := t+1, z := z1}
+%% OT6 ------------------------------------------------------------
+%%     <t1_s2>-----fail(b0:sva_SV0)----><t1_s2>
+
+%%    {t1---cancel(false)-->t1, s2---resume(false)-->s2},   {---:hb_B-->},
+%%    [(:hb_B=resume)/\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
+%%      /\((resume(false))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],
+%%    {}
+%% OT7 ------------------------------------------------------------
+%%     <t1_s2>-----resume----><t1_s2>
+
+%%    {t1---cancel(true)-->t1, s2---resume(true)-->s1},   {---:hb_B-->},
+%%    [(:hb_B=resume)/\((cancel(true))=(cancel(b1:sva_SV1:1:2)))
+%%      /\((resume(true))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],
+%%    {t := 0, z := TopInt}
+%% OT8 ------------------------------------------------------------
+%%     <t1_s2>-----resume----><t1_s1>
+
+%%    {t1---timeout-->t1, s2---timeout-->s3},   {---:hb_E-->},
+%%    [(:hb_E=ask)/\(t in z)],   {t := t+1}
+%% OT9 ------------------------------------------------------------
+%%     <t1_s2>-----ask----><t1_s3>
+
+%%    {t1---tick(z, t, z1)-->t1, s3---fail(zone, false)-->s3},   {---:hb_B-->},
+%%    [(:hb_B=fail(b0:sva_SV0)/\(t<(GET_MAX z))
+%%      /\((tick(z, t, z1))=(tick(z:sva_SV0, t:sva_SV0, z1:sva_SV0)))
+%%      /\((fail(zone, false))=(fail(zone:sva_SV0, b1:sva_SV0)))
+%%      /\(b1:sva_SV0=>b0:sva_SV0)
+%%      /\(z1:sva_SV0=
+%%      (z:sva_SV0  |Intersection| ((b1:sva_SV0?(zone:sva_SV0)TopInt))+t:sva_SV0)))],
+%%    {t := t+1, z := z1}
+%% OT10 ------------------------------------------------------------
+%%     <t1_s3>-----fail(b0:sva_SV0)----><t1_s3>
+
+%%    {t1---cancel(false)-->t1, s3---resume(false)-->s3},   {---:hb_B-->},
+%%    [(:hb_B=resume)/\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
+%%      /\((resume(false))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],   {}
+%% OT11 ------------------------------------------------------------
+%%     <t1_s3>-----resume----><t1_s3>
+
+%%     {s3---reset-->s1},   {---:hb_E-->},     [(:hb_E=ask)],   {}
+%% OT12 ------------------------------------------------------
+%%     <t1_s3>-----reset----><t1_s1>
+
+Now we list the full set of OTs, in latex form, for better
+readability. This comes as a complement to the open automaton in
+Fig. \ref{schema:ArchFailure:OA}, in which we only have a partial view
+of the OTs details.
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=\columnwidth]{TimerOAFullDetailed}
+  \caption{The open Automaton of the Failure Monitor Architecture}
+  \label{schema:ArchFailure:OA}
+\end{figure}
+
+\medskip
+\noindent
+$  OT_1  = \openrule
+{\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
+{\ostate{00} \OTarrow{init} \ostate{11}}
+$
+
+\medskip    
+\noindent
+$  OT_2  = \openrule
+{\{B\mapsto fail(b0)\},\\
+  t<GetMax(z) \land b1=false \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),\\
+  \{z:=z1\} }
+{\ostate{11} \OTarrow{fail} \ostate{11}}
+$
+\medskip
+
+\noindent
+  $  OT_3  = \openrule
+  {\{B\mapsto fail(b0)\},\\
+    t<GetMax(z) \land b1=true \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),\\
+    \{z:=z1\} }
+  {\ostate{11} \OTarrow{fail} \ostate{12}}
+  $
+  \medskip
+
+\noindent
+  $  OT_4  = \openrule
+  {\{B\mapsto resume\},
+    b1=false \land b2=false \land b1=b2
+    \{\}  }
+  {\ostate{11} \OTarrow{resume} \ostate{11}}
+  $
+  \medskip
+
+\noindent
+  $  OT_5  = \openrule
+  {\{E\mapsto ask\},
+    t \in z,
+    \{t:=t+1\}  }
+  {\ostate{11} \OTarrow{ask} \ostate{11}}
+  $
+  \medskip
+
+\noindent
+  $  OT_6  = \openrule
+  {\{B\mapsto fail(b0)\},\\
+    t<GetMax(z) \land b1=false \land b1=>b0 \land z1=(z \cap (b1?zone;TopInt)+t),\\
+    \{t:=t+1, z:=z1\} }
+  {\ostate{12} \OTarrow{fail} \ostate{12}}
+  $
+  \medskip
+
+\noindent
+  $  OT_7  = \openrule
+  {\{B\mapsto resume\},
+    b1=false \land b2=false \land b1=b2,
+    \{\} }
+  {\ostate{12} \OTarrow{resume} \ostate{12}}
+  $
+  \medskip
+
+\noindent
+  $  OT_8  = \openrule
+  {\{B\mapsto resume\},
+    b1=true \land b2=true \land b1=b2, 
+    \{t:=0, z:=TopInt\} }
+  {\ostate{12} \OTarrow{resume} \ostate{11}}
+  $
+  \medskip
+
+\noindent
+  $  OT_9  = \openrule
+  {\{E\mapsto ask\},
+    t \in z,
+    \{t:=t+1\} }
+  {\ostate{12} \OTarrow{ask} \ostate{13}}
+  $
+  \medskip
+
+\noindent
+  $  OT_{10}  = \openrule
+  {\{B\mapsto fail(b0)\},\\
+    t<GetMax(z) \land b1=false \land b1=>b0 \land z1=(z \cap (b1?zone;TopInt)+t),\\
+    \{t:=t+1, z:=z1\} }
+  {\ostate{13} \OTarrow{fail} \ostate{13}}
+  $
+  \medskip
+
+\noindent
+  $  OT_{11}  = \openrule
+  {\{B\mapsto resume\},
+    b1=false \land b2=false \land b1=b2,
+    \{\} }
+  {\ostate{13} \OTarrow{resume} \ostate{13}}
+  $
+  \medskip
+
+\noindent
+  $  OT_{12}  = \openrule
+  {\{E\mapsto reset\},
+    true,
+    \{\} }
+  {\ostate{13} \OTarrow{reset} \ostate{11}}
+  $
+
+  \medskip
+
+  \subsubsection{Properties}
+
+  In Fig. \ref{schema:ArchFailure:OA}, you can see that some
+  properties from appendix \app{properties} do not hold.
+
+  In particular, the first safety property:
+  \begin{equation}*
+    \label{eq:prop:reset:can}
+    \AG \bigl(\PortFail(true) \rightarrow \EU[]{\lnot \PortFail(true)}{(\PortResume(true) \lor \PortReset)}\bigr).
+  \end{equation}
+is not true, because the $OT_2$ loop on state $\ostate{11}$ stays in
+state 11 where you need another $\PortFail(true)$ before enabling a
+resume (or reset). This is because without priorities we can have an
+activity on the dandling ``fail'' port without synchronising with the
+others, even if they are available.
+
+This can be sloved by the version with the Max Progress encoding.
+This modifies both the pLTS transitions, and the synchronisation
+vectors, as shown below:
+
+\small\begin{verbatim}
+SV0: <tick(z, t, z1), fail(zone, bf, b1), fail(b0), _> --> fail(b0),
+         [(b1=>b0)/\((bf/\b0)=>b1)/\(z1=(z |Intersection| ((b1?zone:TopInt)+t)))]
+SV1: <cancel(bc, b1), resume(br, b2), resume, _>-->resume, (b1=b2)/\((bc/\br)=>(b1/\b2))
+SV2: <timeout, timeout, _, ask> --> ask
+SV3: <_, reset, _, reset> --> reset
+SV4: <init, init, _, _> --> init
+
+pLTS: Timer
+- Transition: t0---init-->t1, { t := 0 z := TopInt}
+- Transition: t1---tick(z, t, z1)-->t1, [t<(GET_MAX z)], { t := t+1 z := z1}
+- Transition: t1---cancel(true, false)-->t1, {}
+- Transition: t1---cancel(true, true)-->t1, { t := 0 z := TopInt}
+- Transition: t1---timeout-->t1, [t in z], { t := 0 z := TopInt}
+pLTS: Failure
+- Transition: s0---init-->s1, { zone := minZone,maxZone}
+- Transition: s1---timeout-->s1, {}
+- Transition: s1---resume(false, false)-->s1, {}
+- Transition: s1---fail(zone, true, false)-->s1, {}
+- Transition: s1---fail(zone, true, true)-->s2, {}
+- Transition: s2---fail(zone, false, false)-->s2, {}
+- Transition: s2---resume(true, false)-->s2, {}
+- Transition: s2---resume(true, true)-->s1, {}
+- Transition: s2---timeout-->s3, {}
+- Transition: s3---fail(zone, false, false)-->s3, {}
+- Transition: s3---resume(false, false)-->s3, {}
+- Transition: s3---reset-->s1, {}
+\end{verbatim}
+
+  The new OA is shown in figure \ref{schema:ArchFailure:OA-MaxProgress}.
 
@@
 
+  Here we give the detail of the modification of $OT_2$:
+
 \small\begin{verbatim}
 	    {t1---tick(z, t, z1)-->t1, s1---fail(zone, true, false)-->s1},
-            {B|->fail(b0:sva_SV0:1:1)},
-            [(t<(GET_MAX z))/\((tick(z, t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
-              /\((fail(zone, true, false))=(fail(zone:sva_SV0:1:1, bf:sva_SV0:1:1, b1:sva_SV0:1:1)))
-              /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
-              /\((bf:sva_SV0:1:1/\b0:sva_SV0:1:1)=>b1:sva_SV0:1:1)
-              /\(z1:sva_SV0:1:1=(z:sva_SV0:1:1 |Intersection| ((b1:sva_SV0:1:1?(zone:sva_SV0:1:1):(TopInt))+t:sva_SV0:1:1)))],
+            {B|->fail(b0:sva_SV0)},
+            [(t<(GET_MAX z))/\((tick(z, t, z1))=(tick(z:sva_SV0, t:sva_SV0, z1:sva_SV0)))
+              /\((fail(zone, true, false))=(fail(zone:sva_SV0, bf:sva_SV0, b1:sva_SV0)))
+              /\(b1:sva_SV0=>b0:sva_SV0)
+              /\((bf:sva_SV0/\b0:sva_SV0)=>b1:sva_SV0)
+              /\(z1:sva_SV0=(z:sva_SV0 |Intersection| ((b1:sva_SV0?(zone:sva_SV0):(TopInt))+t:sva_SV0)))],
             {t := t+1, z := z1}
 	OT:2 ------------------------------------------------------------
-		<t1_s1>-----fail(false)----><t1_s1>
-
+		<t1_s1>-----fail(b0:sva_SV0)----><t1_s1>
 \end{verbatim}
 
+As \verb|bf| is true, and \verb|b1| is false, the predicate fragment
+\verb|((bf/\b0)=>b1)| imposes that \verb|b0| is false.
+
+\subsubsection{Scaling-up: composing architectures}
+
+\todoEM{Il faudrait (mais a-t-on le temps?): faire un dessin de la
+  composition au niveau BIP, et au niveau pNet. Un resultat brut, vaguement
+  correct, montre 36 OTs, modulo les petites questions de mon mail de
+  mercredi midi...
+  Au moins dessiner cet automate, et ecrire les proprietes qu'il
+  verifie... }
+
+Primary version of the composed pNet:
+
+\begin{verbatim}
+SV0: <tick(z, t, z1), fail(zone1, b11), fail(zone2, b12), fail1(b01), fail2(b02), _> --> fail(b01, b02), 
+     (z1 = z |Intersection| ((b11?zone1:TopInt)+t) |Intersection| ((b12?zone2:TopInt)+t))
+     /\(b11=>b01)/\(b12=>b02)
+SV1: <cancel(b1), resume(b21), resume(b22), resume1, resume2, _>-->resume, (b1=b21)/\(b1=b22)
+SV2: <timeout, timeout, timeout, _, _, ask>-->ask
+SV3: <_, reset, reset, _, _, reset>-->reset
+SV4: <init, init, init, _, _, _>-->init
+
+pLTS: Timer
+- Transition: t0---init-->t1, { t := 0 z := TopInt}
+- Transition: t1---tick(z, t, z1)-->t1, [t<(GET_MAX z)], { t := t+1 z := z1}
+- Transition: t1---cancel(false)-->t1, {}
+- Transition: t1---cancel(true)-->t1, { t := 0 z := TopInt}
+- Transition: t1---timeout-->t1, [t in z], { t := 0 z := TopInt}
+
+pLTS: FC1
+- Transition: s0---init-->s1, { zone1 := minZone1,maxZone1}
+- Transition: s1---timeout-->s1, {}
+- Transition: s1---resume(false)-->s1, {}
+- Transition: s1---fail(zone1, false)-->s1, {}
+- Transition: s1---fail(zone1, true)-->s2, {}
+- Transition: s2---fail(zone1, false)-->s2, {}
+- Transition: s2---resume(false)-->s2, {}
+- Transition: s2---resume(true)-->s1, {}
+- Transition: s2---timeout-->s3, {}
+- Transition: s3---fail(zone1, false)-->s3, {}
+- Transition: s3---timeout-->s3, {}
+- Transition: s3---resume(false)-->s3, {}
+- Transition: s3---reset-->s1, {}
+
+pLTS: FC2
+- Transition: s0---init-->s1, { zone2 := minZone2,maxZone2}
+- Transition: s1---timeout-->s1, {}
+- Transition: s1---resume(false)-->s1, {}
+- Transition: s1---fail(zone2, false)-->s1, {}
+- Transition: s1---fail(zone2, true)-->s2, {}
+- Transition: s2---fail(zone2, false)-->s2, {}
+- Transition: s2---resume(false)-->s2, {}
+- Transition: s2---resume(true)-->s1, {}
+- Transition: s2---timeout-->s3, {}
+- Transition: s3---fail(zone2, false)-->s3, {}
+- Transition: s3---timeout-->s3, {}
+- Transition: s3---resume(false)-->s3, {}
+- Transition: s3---reset-->s1, {}
+
+INFO  BIPArchFailureTimerMaxV4X2 - Total: 37 SATISFIABLE OTs
+INFO  BIPArchFailureTimerMaxV4X2 -        3136 UNSATISFIABLE OTs
+INFO  BIPArchFailureTimerMaxV4X2 - Total Time: 9111 ms
+\end{verbatim}
+
 \end{document}

### 2019-02-13 2018-Arch-pNets/arch-pNets.tex
Related works: pycots and key-abs

--- 2019-02-12 2018-Arch-pNets/arch-pNets.tex
@@
 
-theorem proving? (too much manual effort) we need an example, we could cite Coqcots and Pycots for reconfiguration == LUDO
+As compositional proof of safety is difficult, some approaches rely on theorem proving to ensure the safety of component operations.
+Coqots and Pycots\cite{BCDLM:CBSE2014} even allow to prove the safety of reconfiguration procedures which are known to be highly difficult to verify, and massively parametrised.
+unfortunately the approach relies on a high expertise and significant efforts from the component user as (s)he must prove manually the safety of the reconfiguration process.
+In this paper, we rely on automatic encoding into a SMT solver making the proof of properties much more automatic, but we cannot prove the safety of the reconfiguration procedure.
 
@@
 
-KeY? (I would call this symbolic execution and assume-guarantee) == LUDO
+In~\cite{DDJO:JLAMP2012}, the authors propose a compositional proof system for distributed objects that is suitable for implementation within the KeY framework~\cite{BHS:Key2007} and uses a Hoare logic approach.
+The approach relies on history invariant for each object, separating local reasoning for proving object invariant from global reasoning that relies on well-formedness of traces.
+Compared to this  approach, we do not  deal with complex history-based specifications because we use interaction specification and SMT-reasoning instead of Hoare logic.
+Also the correctness of the composition is given by the properties of architectures which allows for more flexibility than well-formedness of traces.
 

### 2019-02-13 2018-Arch-pNets/arch-pNets.tex
moved section 4.3

@@
 
-\subsection{SMT encoding of open pNets}
-\label{secn:smt}
+% \subsection{SMT encoding of open pNets}
+% \label{secn:smt}
+
+\section{Case study}
+\label{secn:case-study}
+
+%****************************************************************
+
+\subsection{Verification of the characteristic properties}
+\label{secn:arch:verif}
+
+%% \begin{figure}[t]
+%%   \centering
+%%   \includegraphics[width=\columnwidth]{TimerOpenAut}
+%%   \caption{The open Automaton of the Failure Monitor Architecture}
+%%   \label{schema:ArchFailure:BIP}
+%% \end{figure}
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=0.9\columnwidth]{TimerOADetailed}
+  \caption{The open Automaton of the Failure Monitor Architecture}
+  \label{schema:ArchFailure:OA}
+\end{figure}
 
@@
 
-The encoding into the SMT language involves the definition of the
-action and data domains and operators, and the axiomatisation of
-domain-dependant properties, to allow the SMT engine to be as precise
-as possible (even if it cannot be complete).
-
-The resulting open automaton will later be subject to (symbolic)
-model-checking and equivalence checking algorithms, themselves
-requiring automatic proof assistance. \todoEM{trop flou pour le
-  moment, mais je n'ose pas dire des trucs trop precis... meme si on a
-  deja une implem de la FH-bisim, elle n'est pas validee!}
-
-%\noteEMin{Est-ce qu'on a la place de mettre un exemple de script SMT ici ?}
-
-%****************************************************************
-%****************************************************************
-
-\section{Case study}
-\label{secn:case-study}
-
-%****************************************************************
-
-\subsection{Verification of the characteristic properties}
-\label{secn:arch:verif}
-
-%% \begin{figure}[t]
-%%   \centering
-%%   \includegraphics[width=\columnwidth]{TimerOpenAut}
-%%   \caption{The open Automaton of the Failure Monitor Architecture}
-%%   \label{schema:ArchFailure:BIP}
-%% \end{figure}
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=0.9\columnwidth]{TimerOADetailed}
-  \caption{The open Automaton of the Failure Monitor Architecture}
-  \label{schema:ArchFailure:OA}
-\end{figure}
+%% The encoding into the SMT language involves the definition of the
+%% action and data domains and operators, and the axiomatisation of
+%% domain-dependant properties, to allow the SMT engine to be as precise
+%% as possible (even if it cannot be complete).
+
+%% The resulting open automaton will later be subject to (symbolic)
+%% model-checking and equivalence checking algorithms, themselves
+%% requiring automatic proof assistance. \todoEM{trop flou pour le
+%%   moment, mais je n'ose pas dire des trucs trop precis... meme si on a
+%%   deja une implem de la FH-bisim, elle n'est pas validee!}
 

### 2019-02-13 2016-Weak-FH-Bisim/WeakBisim.tex
revue des preuves

@@
 %\inferrule 
-\forall i \in [0\ldots n].\openrule
+\forall i \in [0..n].\openrule
     {
@@
          {
-           \set{\beta^2},\Pred\,^2,\Post^2 }
-         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
+           \set{\beta^2},\Pred^2,\Post^2 }
+         {s_0^2 \OTarrow {\alpha} s_1^2} \in \mathcal{T}
 \quad \wedge\\
-\forall i \in [0\ldots m].\openrule
-         {
-           \set{\beta^3_i},\Pred\,^3_i,({x^3_{ik}\gets e^3_{ik}})^{k\in K_i}    }
+\forall i \in [0..m].\openrule
+         {
+           \set{\beta^3_i},\Pred^3_i,({x^3_{ik}\gets e^3_{ik}})^{k\in K_i}    }
          {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
@@
 $
-s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
+s=s^1_0 \wedge s^1_{n+1}=s_0^2 \wedge s_1^2 = s^3_0 \wedge s^3_{m+1}=s',
 \displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i}}}
 \\
-\Pred=\bigwedge_{i=0}^n(\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1})\land\Pred\,^2 \bigotimes_{j=0}^{n}\subst{\Post_j^1}\land (\bigwedge_{i=0}^m\Pred_i^3\bigotimes_{j=0}^{i-1}\subst{\Post_j^3}\subst{\Post^2}\bigotimes_{j=0}^{n}\subst{\Post^1_j})\\
-\Post={x^3_{mk}\gets (e^3_{mk}\bigotimes_{j=0}^{m-1}\subst{\Post_j^3}\subst{\Post^2}\bigotimes_{j=0}^{n}\subst{\Post^1_j})^{k\in K_m}}
+\Pred=\bigwedge_{i=0}^n\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\land\Pred^2 \bigotimes_{j=0}^{n}\subst{\Post_j^1}\land\\ 
+~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_i^3\bigotimes_{j=0}^{i-1}\subst{\Post_j^3}\subst{\Post^2}\bigotimes_{j=0}^{n}\subst{\Post^1_j}\Big)\\
+\Post=\big({x^3_{mk}\gets e^3_{mk}\bigotimes_{j=0}^{m-1}\subst{\Post_j^3}\subst{\Post^2}\bigotimes_{j=0}^{n}\subst{\Post^1_j}\big)^{k\in K_m}}
 $
@@
 
-\begin{proof} ($\Rightarrow$) We proceed by induction on  $l=n+m+1$, which is in fact
-the number of transitions with which we  build  a weak transition (introduced in Definition \ref{def:buildweakOT}).
+\begin{proof} ($\Rightarrow$) We proceed by induction on  $l=n+m+1$, which is in fact the number of transitions with which we  build  a weak transition (introduced in Definition \ref{def:buildweakOT}).
 \begin{itemize}
-\item The base case $l=1$, so $n=0$ and $m=0$, then obtain
+\item The base case $l=1$, so $n=0$ and $m=0$, we have:
 \begin{mathpar}
@@
 \end{mathpar} 
-by rule (\WTDeux) we directly conclude 
+by rule (\WTDeux) we can directly conclude the implication: 
  \begin{mathpar}
@@
 \LUDO{je trouve toujours ca pas tres correct le coup $l=n+m+1$ donc $l'=(n+1)+m+1$ ou $l'=n+(m+1)+1$ mais bon comme on dirait que ma proposition plait pas, on verra a la review}
-We consider the case $n'=n+1$, and $m'=m+1$ are similar. Side conditions are omitted for readability. We first focus on the left part of the disjunction. Suppose we have:
-\begin{mathpar}
-\Bigg(\forall i \in [0\ldots n+1].\openrule
+We consider the case $n'=n+1$, and $m'=m+1$ are similar.
+Side conditions are omitted for readability.
+We first focus on the left part of the disjunction.
+Let us consider the sequence of ($n+m+1$) open transitions:
+\begin{mathpar}
+\Big(\forall i \in [0..n].\openrule
     {
@@
          {
-           \set{\beta^2},\Pred\,^2,\Post^2 }
-         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
+           \set{\beta^2},\Pred^2,\Post^2 }
+         {s_0^2 \OTarrow {\alpha} s_1^2} \in \mathcal{T}
 \quad \wedge\\
-\forall i \in [0\ldots m].\openrule
-         {
-           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
+~~\qquad\qquad\forall i \in [0..m].\openrule
+         {
+           \set{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
          {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
-\Bigg) 
-\end{mathpar}
-
-By recurrence hypothesis the theorem is \True~ for any set of transitions of length $l$. In particular, we have
-
-\begin{mathpar}
+\Big) 
+\end{mathpar}
+
+By recurrence hypothesis we suppose that the statement holds for some  set of open transitions of length $l$. In particular, we have:\\
+
+$
 %\mprset {vskip=.5ex}
 %\inferrule 
-\Bigg(\forall i \in [0\ldots n].\openrule
+\Big(\forall i \in [0..n].\openrule
     {
        \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
-         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
-\quad
-\openrule
-         {
-           \set{\beta^2},\Pred\,^2,\Post^2 }
-         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
-\quad \wedge\\
-\forall i \in [0\ldots m].\openrule
-         {
-           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
-         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
-\Bigg)        
-       \bigvee\\   
- \Big(\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)  \implies  {
+         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \,\wedge\,
+\openrule
+         {
+           \set{\beta^2},\Pred^2,\Post^2 }
+         {s_0^2 \OTarrow {\alpha} s_1^2} \in \mathcal{T}
+\, \wedge\\
+~~\hspace{5.25cm}\forall i \in [0..m].\openrule
+         {
+           \set{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
+         {s^3_i \OTarrow {\tau} s^3_{i+1}}\! \in\! \mathcal{T}
+\Big) \\       
+          \bigvee \Big(\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)\!  \implies\!  {
 \openrule
@@
 }
-\end{mathpar}
-
-We need to prove the same implication with  by adding the transition:
+$
+
+We need to prove that   by adding the following open transition the implication remains true:
 \begin{mathpar}
@@
          {
-           \set{\beta},\Pred,\Post}
+           \set{\beta},\Pred\,',\Post\,'}
          {s \OTarrow {\tau} s'} \in \mathcal{T}
@@
 \end{mathpar}
-It will remain so. First by using rule (\WTDeux) we can directly conclude :
-\begin{mathpar}
-
- \openrule
-         {
-           \set{\beta},\Pred,\Post}
+First by using rule (\WTDeux) we have:
+\begin{mathpar}
+
+ \openrule
+         {
+           \set{\beta},\Pred\,',\Post\,'}
          {s \OTarrow {\tau} s'} \in \mathcal{T}
@@
          {
-           \vis{\set{\beta}}\!,\Pred,\Post
+           \vis{\set{\beta}}\!,\Pred\,',\Post\,'
 				 } {s \OTWeakarrow {\tau} s'} \in \WT
@@
 
-On the other hand, by rule (\WTUn) we have
-\begin{mathpar}
- \openrule
-         {
-          \emptyset,\True,\Id(s')
+On the other hand, by rule (\WTUn) we can write the following weak open transition:
+\begin{mathpar}
+ \openrule
+         {
+          \emptyset,\True,\Id(s'')
 				 } {s'' \OTWeakarrow {\tau} s''} \in \WT
@@
 
-Finally by using rule (\WTTrois) we compose the three weak transitions:
+Finally by applying rule (\WTTrois) on  the above weak open transitions:
 
@@
          {
-           \vis{\set{\beta}},\Pred,\Post   }
+           \vis{\set{\beta}},\Pred\,',\Post\,'   }
          {s \OTWeakarrow {\tau} s'} \in \WT
@@
          {
-          \emptyset,\True,\Id(s')
+          \emptyset,\True,\Id(s'')
 				 } {s'' \OTWeakarrow {\tau} s''} \in \WT
 \\
-\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
+\Pred\,''=\Pred\,'\land\Pred\subst{\Post\,'}%\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
 }
@@
           \vis{\set{\beta}} \dotcup \set{\gamma},
-		\Pred,
-				({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K} } 
+		\Pred\,'',\Id(s'')
+				 } 
          {s \OTWeakarrow {\alpha} s''} \in\WT
@@
 
-The right part of the disjunction, i.e.
+The right part of the disjunction, i.e.,
 \begin{mathpar}
@@
 \end{mathpar}
-is handled trivially by rule (\WTUn)
-
+is handled trivially by rule (\WTUn). 
 \end{itemize}
 
-\noindent ($\Leftarrow$) We proceed by structural induction on the rules  building  the weak transition.
+\noindent ($\Leftarrow$) We proceed by structural induction on the rules  building  the weak transition. So we consider the different rules:
 
 \begin{itemize}
-\item Case rule (\WTUn):
+\item Case rule (\WTUn). We have:
 \begin{mathpar}
@@
 \end{mathpar}
-In this case we can directly conclude by the right part of the disjunction.
-\begin{mathpar}
+We can directly conclude by the right part of the disjunction the following:\\
+
+$
 { \openrule
@@
            \emptyset,\True,\Id(s)
-				 } {s \OTWeakarrow {\tau} s} \in \WT
-}\! \implies\! \Big(\alpha = \tau \wedge \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
-\end{mathpar}
-
-\item Case rule (\WTDeux):
+				 } {s \OTWeakarrow {\tau} s}\! \in\! \WT
+}\!\! \implies\!\! \Big(\alpha = \tau \wedge \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
+$
+\item Case rule (\WTDeux). We have:
 \begin{mathpar}
@@
            \set{\beta},\Pred,\Post}
-         {s \OTWeakarrow {\alpha} s'} \in \mathcal{T}         
-\end{mathpar}
-where $\set{\gamma} = \vis{\set{\beta}}$.
-These two cases prove the implication with $n=0$ and $m=0$.
-
-\item Case rule (\WTTrois):
+         {s \OTarrow {\alpha} s'} \in \mathcal{T}         
+\end{mathpar}
+where $\set{\gamma} = \vis{\set{\beta}}$.\\
+
+These two cases above prove the implication with $n=0$ and $m=0$.
+
+\item Case rule (\WTTrois). We have:
 \begin{mathpar}
@@
            \set{\gamma_1},\Pred_1,\Post_1   }
-         {s \OTWeakarrow {\tau} s_1} \in \WT
-\qquad
+         {s \OTWeakarrow {\tau} s'} \in \WT
+\quad
 \openrule
@@
            \set{\gamma_2},\Pred_2,\Post_2  }
-         {s_1 \OTWeakarrow {\alpha} s_2} \in \WT
-\qquad
+         {s' \OTWeakarrow {\alpha} s''} \in \WT
+\quad
 \openrule
@@
            \set{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
-         {s_2 \OTWeakarrow {\tau} s'} \in\WT
+         {s'' \OTWeakarrow {\tau} s'''} \in\WT
 \\
@@
 				({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K} } 
-         {s \OTWeakarrow {\alpha} s'} \in\WT
+         {s \OTWeakarrow {\alpha} s'''} \in\WT
 }
@@
 
-\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau transitions such $n_1=n+m+1$, hence by simplification we have (strictly speaking, by induction we might also have the case $\alpha=\tau\land\set \gamma=\emptyset\land \ldots$ but in this case, \WTUn\ allows us to obtain a similar reduction with $n_1=1$):
+\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau open transitions such $n_1=n+m+1$, hence by simplification we have (strictly speaking, by induction we might also have the case $\alpha=\tau\land\set \gamma=\emptyset\land \ldots$ but in this case, (\WTUn)\ allows us to obtain a similar reduction with $n_1=1$):
 \begin{mathpar}
 %\inferrule{
-\bigg( \openrule
+\openrule
          {
            \set{\gamma_1},\Pred_1,\Post_1   }
-         {s \OTWeakarrow {\tau} s_1} \in\! \WT \bigg)
-\Rightarrow
-\bigg( \forall i \in [0\ldots n_1].\openrule
-    {
-       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
-         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}         \bigg)
+         {s \OTWeakarrow {\tau} s'} \in\! \WT 
+\implies 
+ \forall i \in [0..n_1].\openrule
+    {
+       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
+         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T}
 \end{mathpar}
@@
 $ 
-s=s^1_0 \wedge s^1_{n_1}\!=s_1,
-\displaystyle{\set{\gamma_1}=\mybigdotcup_{i=0}^{n_1} \vis{\set{\beta^1_i}}}, 
-\Pred_1\!=\!\bigwedge_{i=0}^{n_1}\Pred^1_i, \Post_1= \biguplus_{i=0}^{n_1} \Post_i^1\\
+s=s_{10} \wedge s_{1{(n_1+1)}}\!=s',
+\displaystyle{\set{\gamma_1}=\mybigdotcup_{i=0}^{n_1} \vis{\set{\beta_{1i}}}}, 
+\Pred_1\!=\!\bigwedge_{i=0}^{n_1}\Pred_{1i}, \Post_1= \bigotimes_{i=0}^{n_1} \subst{\Post_{1i}}\\
 $
-
-\item Similarly, a series of $m_1=n+m+1$  open transitions can be simplified: 
+\TODO{$\Post_1= \biguplus_{i=0}^{n_1} \Post_{1i}$ or bigotimes?}
+\item Similarly, a series of $m_1$ open transitions such that $m_1=n+m+1$   can be simplified as follows: 
 \begin{mathpar}
 %\inferrule{
-\bigg( \openrule
+\openrule
          {
            \set{\gamma_3},\Pred_3,\Post_3   }
-         {s_2 \OTWeakarrow {\tau} s'} \in\! \WT
-\bigg)
-\Rightarrow
-\bigg( \forall i \in [0\ldots m_1].\openrule
-    {
-       \set{\beta^2_i},\Pred^2_i,\Post^2_i   }
-         {s^2_i \OTarrow {\tau} s^2_{i+1}} \in \mathcal{T}         \bigg)
+         {s'' \OTWeakarrow {\tau} s'''} \in\! \WT
+\implies 
+\forall i \in [0..m_1].\openrule
+    {
+       \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
+         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}        
 \end{mathpar}
@@
 $
-s_2=s^2_0 \wedge s^2_{m_1}=s',
-\displaystyle{\set{\gamma_2}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^2_i}}},
-\Pred_3\!=\!\bigwedge_{i=0}^{m_1}\Pred^2_i,\Post_2\!=\! \biguplus_{i=0}^{m_1} \Post_i^2\\
+s''\!=\!s_{30} \wedge s_{3(m_1+1)}\!=\!s''',
+\displaystyle{\set{\gamma_3}\!=\!\mybigdotcup_{i=0}^{m_1}\vis{\set{\beta_{3i}}}},
+\Pred_3\!=\!\bigwedge_{i=0}^{m_1}\Pred_{3i},\Post_3\!=\!\bigotimes_{i=0}^{m_1} \subst{\Post_{3i}}\\
 $
 
-\item Concerning the middle reduction, by induction hypothesis there exist a set of transitions in $\mathcal{T}$ such that:
-\begin{mathpar}
-\bigg(\openrule
+\item Concerning the middle reduction, by induction hypothesis there exist a set of open transitions in $\mathcal{T}$ such that:
+\begin{mathpar}
+\openrule
          {
            \set{\gamma_2},\Pred_2,\Post_2  }
-         {s_1 \OTWeakarrow {\alpha} s_2} \in\! \WT\bigg)
-\Rightarrow
-\Bigg(\forall i \in [0\ldots n_2].\openrule
-    {
-       \set{\beta^3_i},\Pred^3_i,\Post^3_i   }
-         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}  \wedge
-
-\openrule
-         {
-           \set{\beta^4},\Pred^4,\Post^4 }
-         {s^4 \OTarrow {\alpha} s'^4} \in \mathcal{T}
+         {s' \OTWeakarrow {\alpha} s''} \in\! \WT
+\implies 
+\bigg(\forall i \in [0..n_2].\openrule
+    {
+       \set{\beta_{2i}},\Pred_{2i},\Post_{2i}}
+         {s_{2i} \OTarrow {\tau} s_{2(i+1)}} \in \mathcal{T}  \wedge
+
+\openrule
+         {
+           \set{\beta'},\Pred\,',\Post\,' }
+         {s_2 \OTarrow {\alpha} s_2'} \in \mathcal{T}
  \wedge
-\forall i \in [0\ldots m_2].\openrule
-         {
-           \set{\beta^5_i},\Pred^5_i,({x^5_k\gets e^5_k})^{k\in K}    }
-         {s^5_i \OTarrow {\tau} s^5_{i+1}} \in \mathcal{T}
-\Bigg)         
+\forall i \in [0..m_2].\openrule
+         {
+           \set{\beta_{2i}'},\Pred_{2i}^{\,\prime},({x_k\gets e_k})^{k\in K}    }
+         {s_{2i}' \OTarrow {\tau} s_{2(i+1)}'} \in \mathcal{T}
+\bigg)         
 \end{mathpar}
@@
 $
-s_1=s^3_0 \wedge s^3_{n_2}=s^4 \wedge s'^4 = s^5_0 \wedge s^5_{m_2}=s_2,
-\displaystyle{\set{\gamma_2}=\mybigdotcup_{i=0}^{n_2} \vis{\set{\beta^3_i}} \dotcup  \vis{\set{\beta^4}}  \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^5_i}}}
+s'=s_{20} \wedge s_{2(n_2+1)}=s_2 \wedge s_2' = s_{20}' \wedge s_{2(m_2+1)}'=s''\\
+\displaystyle{\set{\gamma_2}=\mybigdotcup_{i=0}^{n_2} \vis{\set{\beta_{2i}}} \dotcup  \vis{\set{\beta'}}  \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{2i}'}}}
 \\
-\Pred_2=\bigwedge_{i=0}^{n_2}\Pred^3_i\land\Pred\,^4\bigotimes_{i=0}^{n_2}\subst{\Post^3_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred\,^5_i\subst{\Post^4}\Big)\bigotimes_{i=0}^{n_1}\subst{\Post^1_i}
+\Pred_2=\bigwedge_{i=0}^{n_2}\Pred_{2i}\land\Pred\,'\bigotimes_{i=0}^{n_2}\subst{\Post_{2i}}\land \big(\bigwedge_{i=0}^{m_2}\Pred_{2i}^{\,\prime}\subst{\Post\,'}\big)\bigotimes_{i=0}^{n_1}\subst{\Post_{2i}}
 \\
-\Post_2= ({x^5_k\gets (e^5_k\subst {\Post^4})\bigotimes_{i=0}^{n_2}\subst{\Post^3_i}})^{k\in K}
+\Post_2= \big({x_k\gets e_k\subst {\Post\,'}\bigotimes_{i=0}^{n_2}\subst{\Post_{2i}}}\big)^{k\in K}
 $
@@
 ~~\\
-Therefore, we can deduce that:
-\begin{mathpar}
-\bigg( { \openrule
+Therefore, we can deduce that we have:
+\begin{mathpar}
+{ \openrule
          {
@@
 				 } {s \OTWeakarrow {\alpha} s'} \in \WT
-}\bigg)
- \Rightarrow
-\Bigg(\forall i\in [0\ldots(n_1\!+\!n_2)].\openrule
-    {
-       \set{\beta^6_i},\Pred^6_i,\Post^6_i   }
-         {s^6_i \OTarrow {\tau} s^6_{i+1}} \in\mathcal{T} \wedge
-
-\openrule
-         {
-           \set{\beta^7},\Pred^7,\Post^7 }
-         {s^7 \OTarrow {\alpha} s'^7} \in \mathcal{T}
-\wedge
-\forall i \in [0\ldots(m_1\!+\!m_2)].\openrule
-         {\set{\beta^8_i},\Pred^8_i,({x^8_k\gets e^8_k})^{k\in K}    }
-         {s^8_i\OTarrow {\tau} s^8_{i+1}}\in\mathcal{T}\Bigg)  
+}
+ \implies
+\bigg(\forall i\in [0..(n_1\!+\!n_2)].\openrule
+    {
+       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
+         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in\mathcal{T} \wedge
+
+\openrule
+         {
+           \set{\beta^2},\Pred^2,\Post^2 }
+         {s_0^2 \OTarrow {\alpha} s_1^2} \in \mathcal{T}
+\wedge\,
+\forall i \in [0..(m_1\!+\!m_2)].\openrule
+         {\set{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
+         {s^3_i\OTarrow {\tau} s^3_{i+1}}\in\mathcal{T}\bigg)  
 \end{mathpar}
@@
 $
-s_i^6= \left\{
+s_i^1= \left\{
  \begin{array}{ll}
-s_i^1 & \mbox{if }i<n_1\\
-s_{i-n_1}^3 & \mbox{if }i\geq n_1\\
+s_{1i} & \mbox{if }i<n_1\\
+s_{2i-n_1} & \mbox{if }i\geq n_1\\
 \end{array}
-\right. \, \wedge \,
-s_i^8= \left\{
+\right. \quad \wedge \quad
+s_i^3= \left\{
  \begin{array}{ll}
-s_i^2 & \mbox{if }i<m_1\\
-s_{i-m_1}^5 & \mbox{if }i\geq m_1\\
+s_{3i} & \mbox{if }i<m_1\\
+s_{2i-m_1}' & \mbox{if }i\geq m_1\\
 \end{array}
 \right. \\
-s\!=\!s^6_0 \wedge s^6_{n_1+n_2}\!=s^7 \wedge s'^7 = s^8_0 \wedge s^8_{m_1+m_2}\!=\!s'\\
 ~~\\
-\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2}\!\! \vis{\set{\beta^6_i}}
-\dotcup\vis{\set{\beta^7}}\dotcup\!\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta^8_i}}
+s\!=\!s^1_0 \wedge s^1_{(n_1+n_2+1)}\!=s_0^2 \wedge s_1^2 = s^3_0 \wedge s^3_{(m_1+m_2+1)}\!=\!s'''\\
+~~\\
+\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2}\!\! \vis{\set{\beta^1_i}}
+\dotcup\vis{\set{\beta^2}}\dotcup\!\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta^3_i}}
 }\\
-\displaystyle{\Pred=\bigwedge_{i=0}^{n_2}\Pred^6_i\land\Pred^7\bigotimes_{i=0}^{n_2}\subst{\Post^6_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred^6_i\subst{\Post^7}\Big)\bigotimes_{i=0}^{n_1}\subst{\Post^6_i}}
+\displaystyle{\Pred=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred^2\bigotimes_{i=0}^{n_2}\subst{\Post^1_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred^1_i\subst{\Post^2}\Big)\bigotimes_{i=0}^{n_1}\subst{\Post^1_i}}
 \\
-\displaystyle{\Post= ({x^8_k\gets (e^8_k\subst {\Post^7})\bigotimes_{i=0}^{n_2}\subst{ \Post^6_i}})^{k\in K}}
+\displaystyle{\Post= \big({x^3_k\gets e^3_k\subst {\Post^2}\bigotimes_{i=0}^{n_2}\subst{\Post^1_i}}\big)^{k\in K}}
 $\\
-This concludes the inductive step, showing  that the decomposition expressed by the $\Leftarrow$ direction of the lemma is always possible. 
+This concludes the inductive step, showing  that the decomposition expressed by the $\Leftarrow$ direction of the lemma is always possible. \qed
 \end{itemize}
 \end{proof}
------------------------------------------------------
-
-\TODO{develop or delete this sentence} Using this lemma, it is straightforward to see that....
 
@@
 \begin{proof} 
-($\Rightarrow$) Firstly, we prove that Definition \ref{def-Weak-bisim} implies definition above.
-
-Suppose that for any open transition $OT$ in $\mathcal{T}_1$:
- \begin{mathpar}
-     \openrule
-         {
-           \beta_j^{j\in J'_1},\Pred_{OT},\Post_{OT}}
+($\Rightarrow$) Firstly, we prove that Definition \ref{def-Weak-bisim} implies definition above.\\
+Suppose that $\Pred_{s,t}\in \mathcal{R}$ and for any open transition $OT$ in $\mathcal{T}_1$:
+ \begin{mathpar}
+     \openrule
+         {
+           \beta_j^{j\in J},\Pred_{OT},\Post_{OT}}
          {s \OTarrow {\alpha} s'}
@@
 \end{mathpar}
- such that  $\forall x, \{j\in J'|\beta_j\neq\tau\}=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
+ such that  $\forall x, J_{x}=\{j\in J|\beta_j\neq\tau\}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
  and  \\
- $\Pred \land \Pred_{OT}\\
+ $\Pred_{s,t} \land \Pred_{OT}\\
  \implies\!\!\!\displaystyle{\bigvee_{x\in X}}
-   \left(\forall j\in J_x. \vis{\beta_j}=\gamma_{jx}\Rightarrow \Pred_{OT_x}
+   \big(\forall j\in J_x. \vis{\beta_j}=\gamma_{jx}\Rightarrow \Pred_{OT_x}
      \land \alpha\!=\!\alpha_x\land  
-     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
-
-and  suppose we have:
-\begin{mathpar}
-     \openrule
-         {
-           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
+     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\big)$\\
+and  suppose the following statement holds:
+\begin{mathpar}
+     \openrule
+         {
+           \gamma_j^{j\in J},\Pred_{OT},\Post_{OT}}
          {s \OTWeakarrow {\alpha} s'}
@@
 \end{mathpar}
-By using lemma \ref{lem-rel-OT-WOT} we have:
-\begin{mathpar}
-    \openrule
-         {
-           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
+Moreover, by using Lemma \ref{lem-rel-OT-WOT} we know that:
+\begin{mathpar}
+    \openrule
+         {
+           \gamma_j^{j\in J},\Pred_{OT},\Post_{OT}}
          {s \OTWeakarrow {\alpha} s'}
@@
          {
-           {\beta_j^2}^{J^2},\Pred\,^2,\Post^2 }
-         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
+           {(\beta_j^2)}^{j\in J_2},\Pred\,^2,\Post^2 }
+         {s_0^2 \OTarrow {\alpha} s_1^2} \in \mathcal{T}
  \wedge
@@
 s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
-\displaystyle{\gamma_j^{j\in J_1}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i}}}
+\displaystyle{\gamma_j^{j\in J}=\vis{\beta_j^{j\in J}}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i}}}
 \\
-\Pred_{OT}=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\bigotimes_{i=0}^{n}\subst{\Post_i^1}\land (\bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2})\bigotimes_{i=0}^{n}\subst{\Post^1_i}\\
+\Pred_{OT}=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\bigotimes_{i=0}^{n}\subst{\Post_i^1}\land \bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2}\bigotimes_{i=0}^{n}\subst{\Post^1_i}\\
 \Post_{OT}=\biguplus_{i=0}^{m}(\Post_i^3\subst{\Post^2})\bigotimes_{i=0}^{n}\subst{\Post^1_i}
@@
 \begin{enumerate}
-\item First, we have
+\item For the first open transition:
 \begin{mathpar}
@@
        \set{\beta^1},\Pred^1,\Post^1   }
-         {s \OTarrow {\tau} s^1} \in \mathcal{T}          
-\end{mathpar}
-Also, we have $(s,t|\Pred_{s,t})\in\mathcal{R}$. Then
-by  Definition \ref{def-Weak-bisim} we have for an open transition, there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
+         {s_0^1 \OTarrow {\tau} s_1^1} \in \mathcal{T}          
+\end{mathpar}
+we have $(s,t|\Pred_{s,t})\in\mathcal{R}$, hence $(s_0^1,t|\Pred_{s_0^1,t})\in\mathcal{R}$, since $s=s_0^1$.
+By  Definition \ref{def-Weak-bisim} we  can deduce there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
  \begin{mathpar}
@@
 \end{mathpar}
- such that  $\forall x,\{j\in J^2|\beta^1_j\neq\tau\}=J_{x}, (s^1,t_x|\Pred_{s^1,t_x})\in \mathcal{R}$. \\
+ such that  $\forall x,J_{x}=\{j\in J_1|\beta^1_j\neq\tau\}, (s_1^1,t_x|\Pred_{s_1^1,t_x})\in \mathcal{R}$. \\
  $\Pred_{s,t} \land \Pred^1\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
-   \left( \forall j\in J_x. \vis{\beta^1_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
+  \!\! \left( \forall j\in J_x.\vis{\beta^1_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
      \land \alpha_x\!=\!\tau \land  
-     \Pred_{s^1,t_x}\subst{\Post^1}\subst{\Post_{OT_x}}\right)$
+     \Pred_{s_1^1,t_x}\subst{\Post^1}\subst{\Post_{OT_x}}\right)$
 
@@
 \end{mathpar}
-\item Concerning the middle open transition, we have
- \begin{mathpar}
-     \openrule
-         {
-           \beta_j^{J^2},\Pred\,^2,\Post^2 }
-         {s^1 \OTarrow {\alpha} s^2} 
-\end{mathpar}
-For each of the WOTs obtained above, we have the following.
-We have $(s^1,t_x|\Pred_{s^1,t_x})\in \mathcal{R}$. Then
- by Definition \ref{def-Weak-bisim} there exist weak open transitions $\symb{WOT}_{x y}^{x\in X,y\in Y} \subseteq \WT_2$:
+\item Concerning the middle open transition, we have:
+ \begin{mathpar}
+     \openrule
+         {
+           \beta_j^{j \in J_2},\Pred\,^2,\Post^2 }
+         {s_0^2 \OTarrow {\alpha} s_1^2} 
+\end{mathpar}
+For each of the weak open transition obtained above, we have the following.
+We have $(s_1^1,t_x|\Pred_{s_1^1,t_x})\in \mathcal{R}$, then $(s_0^2,t_x|\Pred_{s_0^2,t_x})\in \mathcal{R}$. Again 
+ by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{x y}^{x\in X,y\in Y} \subseteq \WT_2$:
  \begin{mathpar}
@@
 \end{mathpar}
- such that  $\forall x,\{j\in J^2|\beta^2_j\neq\tau\}=J_{x}, 
-(s^2,t_{x y}|\Pred_{s'^2,t_{x y}})\in \mathcal{R}$; \\
- $\Pred_{s^1,t_x} \land \Pred\,^2\\
+ such that  $\forall x,\forall y, J_{xy}=\{j\in J_2|\beta^2_j\neq\tau\}, 
+(s_1^2,t_{x y}|\Pred_{s_1^2,t_{x y}})\in \mathcal{R}$; \\
+ $\Pred_{s_1^1,t_x} \land \Pred\,^2\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}}
-   \left( \forall j\in J_{x y}. \vis{\beta^2_j}=\gamma_{jx y}\Rightarrow \Pred_{OT_{x y}}\land \alpha\!=\!\alpha_{x y} \land  
-     \Pred_{s^2,t_{x y}}\subst{\Post^2}\subst{\Post_{OT_{x y}}}\right)$
+ \!\!  \left( \forall j\in J_{x y}. \vis{\beta^2_j}\!=\!\gamma_{jx y}\Rightarrow \Pred_{OT_{x y}}\!\land \alpha\!=\!\alpha_{x y} \land  
+     \Pred_{s_1^2,t_{x y}}\subst{\Post^2}\subst{\Post_{OT_{x y}}}\right)$
 
 \item 
-And similarly, for an open transition:
+And similarly, for the third  open transition:
      \begin{mathpar}
@@
     {
-       \set{\beta^3},\Pred^3,\Post^3_i   }
-         {s^2 \OTarrow {\tau} s'} \in \mathcal{T}          
-\end{mathpar}
-Additionally, for each $x$ and $y$, we have 
-$(s^2,t_{x y}|\Pred_{s^2,t_{x y}})\in \mathcal{R}$
+       \set{\beta^3},\Pred^3,\Post^3   }
+         {s_0^3 \OTarrow {\tau} s_1^3} \in \mathcal{T}          
+\end{mathpar}
+Additionally, we have 
+$(s_1^2,t_{x y}|\Pred_{s_0^3,t_{x y}})\in \mathcal{R}$, then $(s_0^3,t_{x y}|\Pred_{s_0^3,t_{x y}})\in \mathcal{R}$
 and by Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{x y z}^{x\in X,y\in Y,z\in Z} \subseteq \WT_2$:
@@
 \end{mathpar}
- such that  $\forall z,\{j\in J^3|\beta^3_j\neq\tau\}=J_{3}, 
-(s',t_{x y z}|\Pred_{s',t_{x y z}})\in \mathcal{R}$. \\
- $\Pred_{s^2,t_{x y}} \land \Pred^3\\
+ such that  $\forall x, \forall y, \forall z,J_{xyz}= \{j\in J_3|\beta^3_j\neq\tau\}, 
+(s^3_1,t_{x y z}|\Pred_{s_1^3,t_{x y z}})\in \mathcal{R}$. \\
+ $\Pred_{s_1^2,t_{x y}} \land \Pred^3\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{z\in Z}}
-   \left( \forall j\in J_z. \vis{\beta^3_j}=\gamma_{j x y z}  \Rightarrow \Pred_{OT_{x y z}}
-     \land \alpha_{x y z}\!=\!\tau \land  
-     \Pred_{s',t_{x y z}}\subst{\Post^3}\subst{\Post_{OT_{x y z}}}\right)$
+   \!\left( \forall j\in J_{xyz}. \vis{\beta^3_j}\!=\!\gamma_{j x y z} \! \Rightarrow\! \Pred_{OT_{x y z}}\!
+     \land\! \alpha_{x y z}\!=\!\tau \land  
+     \Pred_{s^3_1,t_{x y z}}\subst{\Post^3}\subst{\Post_{OT_{x y z}}}\right)$
 
@@
 
-On other hand, by applying (\WTTrois)~rule  on each  $\symb{WOT}_x$ we have:
+Moreover, by applying (\WTTrois)~rule on the resulting $\symb{WOT}$s we have:
 
@@
  \end{mathpar}
-We need to prove:\\
+So we need to prove that the following holds:\\
 $\Pred_{s,t} \land \Pred\\
@@
      \Pred_{s',t_{x y z}}\subst{\Post_{OT}}\subst{\Post\,}\right)$
-Recall that:\\
+We recall that we have:\\
 $\Pred_{OT}= \Pred^1 \wedge \Pred^2\subst{\Post^1} \wedge \Pred^3\subst{\Post^2}\subst{\Post^1}$\\
 $\Post_{OT}=\Post^3\subst{\Post^2}\subst{\Post^1}$\\
-Let's start with the following formula.\\
+Let's start with the statement:\\
 $\Pred_{s,t} \land \Pred^1\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
-   \left( \forall j\in J_x. \vis{\beta^1_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
+ \! \! \left( \forall j\in J_x. \vis{\beta^1_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
      \land \alpha_x\!=\!\tau \land  
-     \Pred_{s^1,t_x}\subst{\Post^1}\subst{\Post_{OT_x}}\right)$\\
-Applying the conjunction  $\Pred^2\subst{\Post^1}$ to both sides of the implication, we get:\\  
+     \Pred_{s_1^1,t_x}\subst{\Post^1}\subst{\Post_{OT_x}}\right)$\\
+The conjunction with the term $\Pred^2\subst{\Post^1}$ of the both sides of the implication, we get:\\  
 $(\Pred_{s,t} \land \Pred^1)\wedge\Pred^2\subst{\Post^1}\\
- \hspace{1cm} \implies\!\!\! \Big(\displaystyle{\bigvee_{x\in X}}
-   \left( \forall j\in J_x. \vis{\beta^1_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
+ \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
+  \!\! \left( \forall j\in J_x. \vis{\beta^1_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
      \land \alpha_x\!=\!\tau \land  
-     \Pred_{s^1,t_x}\subst{\Post^1}\subst{\Post_{OT_x}}\right) \Big) \wedge\Pred^2\subst{\Post^1} \subst{\Post_{OT_x}}  \\
+     \Pred_{s_1^1,t_x}\subst{\Post^1}\subst{\Post_{OT_x}}\right) \wedge\Pred^2\subst{\Post^1} \subst{\Post_{OT_x}}  \\
 $
-Note because of the domain independence of the substitution, we have just added  $\subst{\Post_{OT_x}}$ on the right side. A little rewriting gives:\\
+Note because of the domain independence of the substitution, we have also added the substitution $\subst{\Post_{OT_x}}$ on the right side of the implication without affecting the validity of the statement.
+Hence a little rewriting gives:\\
 $(\Pred_{s,t} \land \Pred^1)\wedge\Pred^2\subst{\Post^1}\\
- \hspace{1cm} \implies\!\!\! \Big(\displaystyle{\bigvee_{x\in X}}
-   \left(\forall j\in J_x. \vis{\beta^1_j}\!=\!\gamma_{jx}\Rightarrow \Pred_{OT_x}
-     \!\land\! \alpha_x\!=\!\tau\land(\Pred_{s^1,t_x}\wedge\Pred^2)\subst{\Post^1}\subst{\Post_{OT_x}} \right)\Big)$\\
-By replacing $(\Pred_{s^1,t_x}\wedge\Pred^2)$ sub-term,  the formula becomes: \\
+ \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
+\!\!   \left(\forall j\in J_x. \vis{\beta^1_j}\!=\!\gamma_{jx}\Rightarrow \Pred_{OT_x}
+     \!\land\! \alpha_x\!=\!\tau\land(\Pred_{s_1^1,t_x}\wedge\Pred^2)\subst{\Post^1}\subst{\Post_{OT_x}} \right)$\\
+By replacing the inner sub-term $(\Pred_{s_1^1,t_x}\wedge\Pred^2)$ by the consequent of the corresponding implication given in case 2,  the formula becomes: \\
 $(\Pred_{s,t} \land \Pred^1)\wedge\Pred^2\subst{\Post^1}\\
- \hspace{1cm} \implies\!\!\! \Big(\displaystyle{\bigvee_{x\in X}}
-   (\forall j\in J_x. \vis{\beta^1_j}\!\!=\!\!\gamma_{jx}  \Rightarrow \Pred_{OT_x}
-     \!\land\! \alpha_x\!=\!\tau \land \Big(\displaystyle{\bigvee_{y\in Y}}
+ \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
+   \!\!\Big(\forall j\in J_x. \vis{\beta^1_j}\!\!=\!\!\gamma_{jx}  \Rightarrow \Pred_{OT_x}
+     \!\land\! \alpha_x\!=\!\tau \land\Big(\displaystyle{\bigvee_{y\in Y}}
    ( \forall j\in J_{x y}.
-\vis{\beta^2_j}\!\!=\!\!\gamma_{jx y}\Rightarrow \Pred_{OT_{x y}}\land \alpha\!=\!\alpha_{x y} \land \Pred_{s^2,t_{x y}}\subst{\Post^2}\subst{\Post_{OT_{x y}}})\Big)\subst{\Post^1} \subst{\Post_{OT_x}} )\Big)$\\
+\vis{\beta^2_j}\!\!=\!\!\gamma_{jx y}\Rightarrow\\~~\qquad\quad \Pred_{OT_{x y}}\land \alpha\!=\!\alpha_{x y}\!
+\land \Pred_{s_1^2,t_{x y}}\subst{\Post^2}\subst{\Post_{OT_{x y}}})\Big)\subst{\Post^1} \subst{\Post_{OT_x}} \Big)$\\
 Furthermore, the rewriting of the implication  gives:\\
@@
 \vis{\beta^1_j}\!\!=\!\!\gamma_{jx} \land  \forall j \in J_{x y}.
-\vis{\beta^2_j}\!\!=\!\!\gamma_{jx y}\Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post^1} \subst{\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \land \Pred_{s^2,t_{x y}}\subst{\Post^2}\subst{\Post^1}\subst{\Post_{OT_{x y}}} \subst{\Post_{OT_x}}\Big)$\\
-Finally, applying the conjunction $\Pred^3\subst{\Post^2}\subst{\Post^1}$ to both sides of the implication and rewriting, we get:\\
+\vis{\beta^2_j}\!\!=\!\gamma_{jx y}\Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \\\subst{\Post^1} \subst{\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \land \Pred_{s_1^2,t_{x y}}\subst{\Post^2}\subst{\Post^1}\subst{\Post_{OT_{x y}}} \subst{\Post_{OT_x}}\Big)$\\
+Finally, the conjunction with the term $\Pred^3\subst{\Post^2}\subst{\Post^1}$ of the both sides of the implication and rewriting, we get:\\
 $(\Pred_{s,t} \land \Pred^1)\wedge\Pred^2\subst{\Post^1} \land \Pred^3\subst{\Post^2}\subst{\Post^1}\\
@@
 \vis{\beta^2_j}\!=\!\gamma_{jx y} \Rightarrow \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \alpha_x\!=\!
-\tau \land \alpha\!=\! \alpha_{x y} \land (\Pred_{s^2,t_{xy}} \land  \Pred^3) \subst{\Post^2}
+\tau \land \alpha\!=\! \alpha_{x y} \land (\Pred_{s_1^2,t_{xy}} \land  \Pred^3) \subst{\Post^2}
 \subst{\Post^1}\subst{\Post_{OT_{x y}}} 
 \subst{\Post_{OT_x}} \Big)$\\ 
-Note because of the domain independence of the substitution, we have deleted $\subst{\Post^1}$, and  we have added  $\subst{\Post_{OT_{x y}}}\subst{\Post_{OT_x}}$ on the right side sub-terms.
-By replacing $(\Pred_{s^2,t_{xy}} \land  \Pred^3)$, we get:\\
+Again because of the domain independence of the substitution, we deleted $\subst{\Post^1}$, and  we have added  $\subst{\Post_{OT_{x y}}}\subst{\Post_{OT_x}}$ on the right side of the implication.
+Finally, by replacing $(\Pred_{s_1^2,t_{xy}} \land  \Pred^3)$
+by the consequent of the corresponding implication given in case 3, we get:\\
 $(\Pred_{s,t} \land \Pred^1)\land \Pred^2\subst{\Post^1} \land \Pred^3\subst{\Post^2}\subst{\Post^1}\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} \displaystyle{\bigvee_{z\in Z}} 
-\Big(\forall j\in J_x.\vis{\beta^1_j}\!\!=\!\!\gamma_{jx} \land  \forall j \in J_{x y}.
-\vis{\beta^2_j}\!\!=\!\!\gamma_{jx y} \forall j\in J_{x y z}.
-\vis{\beta^3_j}\!\!=\!\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}} \subst{\Post_{OT_x}} \land \alpha_x\!=\!
-\tau \land \alpha\!=\!\alpha_{x y} \land \alpha_{x y z}\!=\!\tau \land \Pred_{s',t_{x y z}}  \underbrace{\subst{\Post^3}\subst{\Post^2}
+\Big(\forall j\in J_x.\vis{\beta^1_j}\!\!=\!\!\gamma_{jx} \land\!
+\forall j \!\in\!
+J_{x y}.\vis{\beta^2_j}\!\!=\!\!\gamma_{jx y} \forall j\!\in\!
+J_{x y z}.
+\vis{\beta^3_j}\!\!=\!\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\!\subst{\Post_{OT_{x y}}} \subst{\Post_{OT_x}} \land \alpha_x\!=\!
+\tau \!\land \alpha\!=\!\alpha_{x y} \land \alpha_{x y z}\!=\!\tau \land \Pred_{s^3_1,t_{x y z}}  \underbrace{\subst{\Post^3}\subst{\Post^2}
 \subst{\Post^1}}_{\subst{\Post_{OT}}}\subst{\Post_{OT_{x y z}}}\subst{\Post_{OT_{x y}}} \subst{\Post_{OT_x}} \Big)$
-Therefore, we conclude:\\
+Therefore, having $s^3_1=s'$ we can conclude:\\
 $(\Pred_{s,t} \land \Pred^1)\land \Pred^2\subst{\Post^1} \land \Pred^3\subst{\Post^2}\subst{\Post^1}\\
@@
 \subsection{Composition properties}
-\TODO{Ludo: in the next 2 theorems I have a doubt about the biguplus of post p : not sure they should be disjoint, but else we need to do a complex composition  of posts}
+
 \begin{lemma}[Weak OT decomposition]\label{lem-decomposeWOT} 
@@
 		\land \!\!\bigwedge_{p=0}^n(\alpha_p= \beta_p\land \Pred_p) \qquad\text{and~}
-\Post=\Post\,'\uplus\!\! \biguplus_{p=0}^n
+\Post=\Post\,'\uplus \bigotimes_{p=0}^n
 		\Post_p  
@@
 By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
-$ \forall p\! \in [0\ldots m_1]\,		
+$ \forall p\! \in [0..m_1]\,		
 	P[Q]_{j_0}\!\models		
@@
     {
-       (\set{\beta^1_p}),\Pred^1_p,\Post^1_p   }
+       \set{\beta^1_p},\Pred^1_p,\Post^1_p   }
          {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$,  $\qquad  P[Q]_{j_0}	\models \openrule
@@
 and 
- $\forall p \in [0\ldots m_2] \,\, P[Q]_{j_0}\!\models \openrule
-         {
-           (\set{\beta^3_p}),\Pred\,^3_p, \Post_p^3   }
+ $\forall p \in [0..m_2] \,\, P[Q]_{j_0}\!\models \openrule
+         {
+           \set{\beta^3_p},\Pred\,^3_p, \Post_p^3   }
          {\ostate{u^{l\in L}_{pl}} \OTarrow {\tau} \ostate{u^{l\in L}_{(p+1)l}}}
@@
 $\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i}}}\\
-\Pred=\bigwedge_{i=0}^{m_1}\big(\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land \bigwedge_{i=0}^{m_2}\Pred_i^3\big((\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1})\big)\\
-\Post=\bigotimes_{i=0}^{m_2}\Post^3_i\big(\subst{\Post^2}\bigotimes_{j=0}^{m_1}\subst{\Post^1_j}\big)
+\Pred=\bigwedge_{i=0}^{m_1}\!\big(\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land \bigwedge_{i=0}^{m_2}\!\Pred_i^3\big(\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\big)\\
+\Post=\bigotimes_{i=0}^{m_2}\Post^3_i\subst{\Post^2}\bigotimes_{j=0}^{m_1}\subst{\Post^1_j}
 $\\
 
-We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$:
+\noindent We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$:
 \begin{enumerate}
@@
     {
-       (\set{\beta^1_p}),\Pred^1_p,\Post^1_p   }
+       \set{\beta^1_p},\Pred^1_p,\Post^1_p   }
          {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$ \\
@@
 				(\beta^1_{pj})^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
-				{(\Pred^1_p)}',  
-				{(\Post^1_p)}'}
+				{\Pred^{1a}_p},  
+				{\Post^{1a}_p}}
 			{\ostate{s_{p l}^{l\in L\setminus L_Q}} \OTarrow {\tau}
@@
 			{
-				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{(\Pred^1_p)}''},  
-				{{(\Post^1_p)}''}}
-				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
+				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred^{1b}_p}},  
+				{{\Post^{1b}_p}}}
+				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha^1_{p}}
 				\ostate{s_{(p+1)l}^{l\in L_Q}}}
@@
 $
-such that  $\Pred^1_p \iff {(\Pred^1_p)}'
-		\land {(\Pred^1_p)}''\land \alpha_p=\beta_{pj_0}$, $\Post^1_p={(\Post^1_p)}'\uplus 
-		{(\Post^1_p)}''$ where ${{(\Post^1_p)}''}$ is the restriction of $\Post^1_p$ over variables of $\Leaves(Q)$.\\
+such that  $\Pred^1_p \iff {\Pred^{1a}_p}
+		\land {\Pred^{1b}_p}\land \alpha^1_p=\beta^1_{pj_0}$, $\Post^1_p={\Post^{1a}_p}\uplus 
+		{\Post^{1b}_p}$ where ${{\Post^{1b}_p}}$ is the restriction of $\Post^1_p$ over variables of $\Leaves(Q)$.\\
 Else $Q$ does not move and we have: \\
@@
 				(\beta^1_{pj})^{j\in (J\setminus \Holes(Q)) }, 
-				{(\Pred^1_p)}',  
-				{(\Post^1_p)}'}
+				{\Pred^{1a}_p},  
+				{\Post^{1a}_p}}
 			{\ostate{(s_{p l})^{l\in L\setminus L_Q}} \OTarrow {\tau}
@@
 				(\beta^2_j)^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
-				{\Pred^2}',  
-				{\Post^2}'}
+				{\Pred^{2a}},  
+				{\Post^{2a}}}
 			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
@@
 			{
-				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {\Pred^2}'',  
-				{\Post^2}''}
-			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'}
+				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {\Pred^{2b}},  
+				{\Post^{2b}}}
+			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha^2}
 				\ostate{t_l'^{\,l\in L_Q}}}
@@
 $\\
-such that  $\Pred^2 \iff {\Pred}\,'
-		\land {\Pred^2}''\land \alpha'=\beta_{j_0}$, $\Post^2={\Post^2}'\uplus 
-		{\Post^2}''$ where ${\Post^2}''$ is the restriction of $\Post^2$ over variables of $\Leaves(Q)$.
+such that  $\Pred^2 \iff {\Pred^{2a}}
+		\land {\Pred^{2b}}\land \alpha^2=\beta^2_{j_0}$, $\Post^2={\Post^{2a}}\uplus 
+		{\Post^{2b}}$ where ${\Post^{2b}}$ is the restriction of $\Post^2$ over variables of $\Leaves(Q)$.
 
@@
 				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
-				\Pred\,',  
-				\Post\,'}
+				\Pred^a,  
+				\Post^a}
 			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
@@
 where for all $l\in L$:\\
-$s_l=s_{0l} \wedge s_{{(m_1+1)}l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)}l=s'_l$\\
+$s_l=s_{0l} \wedge s_{(m_1+1)l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)l}=s'_l$\\
 $\forall j\in (J\setminus \Holes(Q))\cup \{j_0\},
@@
 \\
-\Pred\,'=\bigwedge_{i=0}^{m_1}
-({\Pred_i^1}'\bigotimes_{j=0}^{i-1}\subst{{\Post_j^1}'})
-\land{\Pred^2}'\bigotimes_{i=0}^{m_1}\subst{{\Post_i^1}'}\land 
-(\bigwedge_{i=0}^{m_2}{\Pred\,^3_i}'(\bigotimes_{j=0}^{i-1}\subst{{\Post^3_j}'})\subst{{\Post^2}'}(\bigotimes_{j=0}^{m_1}\subst{{\Post^1_j}'}))\\
-\Post'=(\bigotimes_{i=0}^{m_2}{\Post^3_i}')\subst{{\Post^2}'}\bigotimes_{j=0}^{m_1}\subst{{\Post^1_j}'}
+\Pred^{a}=\big(\bigwedge_{i=0}^{m_1}
+{\Pred_i^{1a}}\bigotimes_{j=0}^{i-1}\subst{{\Post_j^{1a}}}\big)
+\land{\Pred^{2a}}\bigotimes_{i=0}^{m_1}\subst{{\Post_i^{1a}}}\land \\
+~~\qquad\quad\big(\bigwedge_{i=0}^{m_2}{\Pred_i^{3a}}\bigotimes_{j=0}^{i-1}\subst{{\Post_j^{3a}}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}}\big)\\
+\Post^a=\bigotimes_{i=0}^{m_2}{\Post_i^{3a}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}}
 $
@@
 Concerning $Q$, we consider only the paths for which it moves.
-So for each, state such that we have $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}}$, we skip the state $\ostate{({s}_{(p+1) l})^{l\in L_Q}}$ and  we rename all its following states  $\ostate{(s_{p})_l^{l\in L_Q}}$ by $\ostate{({s}_{(p-1) l})^{l\in L_Q}}$.
+So for all states for which we have $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}}$, we skip the state $\ostate{({s}_{(p+1) l})^{l\in L_Q}}$ and  we rename all its following states  $\ostate{(s_{p})_l^{l\in L_Q}}$ by $\ostate{({s}_{(p-1) l})^{l\in L_Q}}$.
 We proceed in the same way as for states named $u$.
@@
 So we have: \\
-$\forall p \in [0\ldots n_1] Q\models{\openrule
-			{
-				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred^1_p}''},  
-				{{\Post^1_p}''}}
-				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
+$\forall p\! \in\! [0..n_1] Q\models{\openrule
+			{
+				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^{1b}}},  
+				{{\Post_p^{1b}}}}
+				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha^1_{p}}
 				\ostate{s_{(p+1)l}^{l\in L_Q}}}
@@
 and
-$\forall p \in [0\ldots n_2] Q\models{\openrule
-			{
-				(\beta^3_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred^3_p}''},  
-				{{\Post^3_p}''}}
-				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha'_{p}}
+$\forall p \in [0..n_2] Q\models{\openrule
+			{
+				(\beta^3_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^{3b}}},  
+				{{\Post_p^{3b}}}}
+				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha^3_{p}}
 				\ostate{u_{(p+1)l}^{l\in L_Q}}}
@@
 
-$\forall p \in [0\ldots (n_1+n_2+2)]\,\, Q\models{\openrule
-			{
-				(\beta_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p}\!\!''},  
-				{{\Post_p}\!\!''}}
+$\forall p \in [0..(n_1+n_2+2)]\,\, Q\models{\openrule
+			{
+				(\beta_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^b}},  
+				{{\Post_p^b}}}
 				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
@@
 We can decompose each of the $n$ subsequences; the length of the subsequence number $k$ is $n_k$,  and the subsequence is made of the following OTs:\\
-$\forall p \in [0\ldots (n'-1)] Q\models{\openrule
-			{
-				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred^1_p}''},  
-				{{\Post^1_p}''}}
+$\forall p\! \in\! [0..(n'-1)] Q\models{\openrule
+			{
+				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^{1b}}},  
+				{{\Post_p^{1b}}}}
 				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
@@
 			{
-				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred^2}''},  
-				{{\Post^2}''}}
-				{\ostate{v_{n'l}^{l\in L_Q}} \OTarrow {\alpha_k}
+				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred^{2b}}},  
+				{{\Post^{2b}}}}
+				{\ostate{v_{n'l}^{l\in L_Q}} \OTarrow {\alpha'_k}
 				\ostate{v_{(n'+1)l}^{l\in L_Q}}}
@@
 and
-$\forall p \in [(n'+1)\ldots (n_k-1)]\,\, Q\models{\openrule
-			{
-				(\beta^3_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred^3_p}''},  
-				{{\Post^3_p}''}}
+$\forall p \in [(n'+1)..(n_k-1)]\,\, Q\models{\openrule
+			{
+				(\beta^3_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^{3b}}},  
+				{{\Post_p^{3b}}}}
 				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
@@
 			{
-			(\gamma'_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
-				{{\Post_k}}}
+			(\gamma'_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred^b_k}},  
+				{{\Post^b_k}}}
 			{\ostate{v_{l}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
@@
 \\
-\Pred_k=\big(\!\!\!\bigwedge_{i=0}^{(n'-1)}\!\!
-{\Pred_i^1}''\bigotimes_{j=0}^{(i-1)}\subst{{\Post_j^1}''}\big)
-\land{\Pred^2}''\bigotimes_{i=0}^{(n'-1)}\subst{{\Post_i^1}''}\land\\
-~\qquad\qquad\qquad\Big(\!\!\!\bigwedge_{i=(n'+1)}^{(n_k-1)}\!\!\!{\Pred^3_i}''\bigotimes_{j=n'+1}^{(i-1)}\subst{{\Post^3_j}''}\subst{{\Post^2}''}\bigotimes_{i=0}^{(n'-1)}\subst{{\Post^1_i}''}\Big)\\
-\Post_k=\Big(\!\!\!\!\bigotimes_{i=(n'+1)}^{(n_k-1)}{\Post^3_i}''\subst{{\Post^2}''}\bigotimes_{i=0}^{(n'-1)}\subst{{\Post^1_i}''}\Big)
+\Pred^b_k=\Big(\!\!\!\bigwedge_{i=0}^{(n'-1)}\!\!
+{\Pred_i^{1b}}\bigotimes_{j=0}^{(i-1)}\subst{{\Post_j^{1b}}}\Big)
+\land\Big({\Pred^{2b}}\bigotimes_{i=0}^{(n'-1)}\subst{{\Post_i^{1b}}}\Big)\land\\
+~\qquad\qquad\Big(\!\!\!\bigwedge_{i=(n'+1)}^{(n_k-1)}\!\!\!{\Pred_i^{3b}}\bigotimes_{j=n'+1}^{(i-1)}\subst{{\Post_j^{3b}}}\subst{{\Post^{2b}}}\bigotimes_{i=0}^{(n'-1)}\subst{{\Post_i^{1b}}}\Big)\\
+\Post^b_k=\bigotimes_{i=(n'+1)}^{(n_k-1)}\!\!\!{\Post_i^{3b}}\Big(\subst{{\Post^{2b}}}\bigotimes_{i=0}^{(n'-1)}\subst{{\Post_i^{1b}}}\Big)
 $\\
@@
 
-\TODO{link gamma j 0 with the alpha k ; this ises the visible abstraction and the ewautaions of 1,2,3 decomposition}
-
-From cases 1, 2 and 3 we have for all $k\in [0\ldots n]$, $\beta_{kj_0}=\alpha_k$. Moreover, we have:\\ 
-$\displaystyle{\gamma_{j_0}}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{i{j_0}}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{i{j_0}}}=(\alpha'_k)^{k\in 1..n}=\{\alpha_p|p\in [0..m_1+m_2+1] \land \alpha_p\neq \tau\}$
+\TODO{A revoir pas correct!: From cases 1, 2 and 3 we have for all $k\in [0\ldots n]$, $\beta_{kj_0}=\alpha_k$. Moreover,} \\
+
+We have: 
+$\displaystyle{\gamma_{j_0}}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{i{j_0}}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{i{j_0}}}=[\alpha'_0..
+\alpha'_n]$, indeed $\displaystyle{\gamma_{j_0}}$ is a a list of $\alpha_p$ such that $p\in [0..n_1+n_2+1] \land \alpha_p\neq \tau$.
 %$\displaystyle{\gamma_{kj_0} }=\mybigdotcup_{i=0}^{(n'-1)}\!\!\vis{\beta^1_{ij_0}}\,\dotcup\,\vis{\set{\beta^2_{j_0}}}\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij_0}}$ \TODO{?????}\\
 
-For  $\gamma_{j_0}=[\beta_0..\beta_n]$ we have $n$ weak open transitions  $\symb{WOT}_k$ such that $k\in [0\ldots n]$.
-Therefore, we can conclude that we have for all $k\in [0\ldots n]$:  
+For  $\gamma_{j_0}=[\beta_0..\beta_n]$ such that $\beta_i=\alpha'_i$ we have $n$ weak open transitions  $\symb{WOT}_k$ such that $k\in [0..n]$.
+Therefore, we can conclude that we have for all $k\in [0..n]$:  
 \begin{mathpar}
@@
   $\Pred \iff \Pred\,'
-		\land \displaystyle{\bigvee_{p=0}^n}(\alpha_p= \beta_{pj_0}\land \Pred_p), \text{and~}
-\Post=\Post\,'\uplus\biguplus_{p=0}^n
-		\Post_p \quad$
-
-\TODO{I stopped there!}
+		\land \displaystyle{\bigwedge_{p=0}^n}(\alpha_p= \beta_{pj_0}\land \Pred_p), \text{and~}
+\Post=\Post\,'\uplus\bigotimes_{p=0}^n
+		\Post_p \quad$  \\
+------------------------------------------------------\\
+We have:\\
+$\Pred=\displaystyle{\bigwedge_{i=0}^{m_1}\!\big(\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land \bigwedge_{i=0}^{m_2}\!\Pred_i^3\big(\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}}\big)$\\
+By replacing ${\Pred^{1}_i}$,  $\Pred^2$, and ${\Pred^{3}_i}$ we obtain:\\
+$\Pred \iff\displaystyle{\bigwedge_{i=0}^{m_1}({\Pred^{1a}_i}
+		\land {\Pred^{1b}_i}\land \alpha^1_i=\beta^1_{ij_0}) \bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land}\\
+~~\qquad\qquad\qquad({\Pred^{2a}}\land {\Pred^{2b}}\land \alpha^2=\beta^2_{j_0})	\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land\\
+~~\qquad\qquad\bigwedge_{i=0}^{m_2} ({\Pred^{3a}_i}\land {\Pred^{3b}_i}\land \alpha^3_i=\beta^3_{ij_0})\big(\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\big)
+		$\\
+By distribution of the substitution operation over the logical operator we can deduce:\\
+$\Pred\iff \displaystyle{\big(\bigwedge_{i=0}^{m_1}
+{\Pred_i^{1a}}\bigotimes_{j=0}^{i-1}\subst{{\Post_j^{1a}}}\big)
+\land{\Pred^{2a}}\bigotimes_{i=0}^{m_1}\subst{{\Post_i^{1a}}}\land} \\
+~~\qquad\qquad\quad\big(\bigwedge_{i=0}^{m_2}{\Pred_i^{3a}}\bigotimes_{j=0}^{i-1}\subst{{\Post_j^{3a}}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}}\big) \land\\	
+~\qquad\qquad\quad\bigwedge_{i=0}^{m_1}({\Pred^{1b}_i}\land \alpha^1_i=\beta^1_{ij_0}) \bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land({\Pred^{2b}}\land \alpha^2=\beta^2_{j_0})	\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land\\
+~\qquad\qquad\quad\bigwedge_{i=0}^{m_2} ({\Pred^{3b}_i}\land \alpha^3_i=\beta^3_{ij_0})\big(\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\big)
+$\\		
+Therefore, we have:\\
+$\Pred\iff \Pred^a \wedge\\
+~~\qquad\qquad\quad\displaystyle{\big(\bigwedge_{i=0}^{m_2}{\Pred_i^{3a}}\bigotimes_{j=0}^{i-1}\subst{{\Post_j^{3a}}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}}\big) \land}\\	
+~\qquad\qquad\quad\bigwedge_{i=0}^{m_1}({\Pred^{1b}_i}\land \alpha^1_i=\beta^1_{ij_0}) \bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land({\Pred^{2b}}\land \alpha^2=\beta^2_{j_0})	\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land\\
+~\qquad\qquad\quad\bigwedge_{i=0}^{m_2} ({\Pred^{3b}_i}\land \alpha^3_i=\beta^3_{ij_0})\big(\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\big)
+$
+
+\TODO{Je n'ai pas d'idee comment simplifier le reste!}\\
+For the postcondition we have:\\
+$\Post=\displaystyle{\bigotimes_{i=0}^{m_2}\Post^3_i\subst{\Post^2}\bigotimes_{j=0}^{m_1}\subst{\Post^1_j}}$\\
+By replacing ${\Post^{1}_i}$,  $\Post^2$, and ${\Post^{3}_i}$ we obtain:\\
+$\Post= \displaystyle{\bigotimes_{i=0}^{m_2}\subst{{\Post^{3a}_i}\uplus 
+		{\Post^{3b}_i}} \subst{{\Post^{2a}}\uplus 
+		{\Post^{2b}}} \bigotimes_{j=0}^{m_1}\subst{ {\Post^{1a}_i}\uplus 
+		{\Post^{1b}_i}}}\\
+~~\qquad= \bigotimes_{i=0}^{m_2}{\Post_i^{3a}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}} \uplus \ldots  $
 \end{proof}
+\TODO{l'autre terme a voir!}
 
@@
 \forall j\in J_p,\,\gamma_j= \mathop{\dot{\bigcup}}_{p\in [0..n]} \gamma_{p j} 
+\Post\,'=\Post\uplus\bigotimes_{p=0}^{n}
+		\Post_p 
 \end{mathpar}
@@
 			\gamma_j^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
-			\Pred\,',  
-			\Post\uplus\biguplus_{p\in[0..n]}
-		\Post_p  }
+			\Pred\,',  \Post\,'
+			 }
 		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}

### 2019-02-13 2018-Arch-pNets/arch-pNets.tex
Removed priorities from Section 3

@@
 \newcommand{\EF}[1][\ ]{\ensuremath{\mathtt{EF}#1}}
+\newcommand{\EX}[1][\ ]{\ensuremath{\mathtt{EX}#1}}
 \newcommand{\AW}[3][\ ]{\ensuremath{\mathtt{A}\left[#2\ \mathtt{W}\ #3\right]#1}}
@@
 
+\addSB{This section presents the extension of the theory of
+  architectures \cite{AttieBBJS16-architectures-faoc} with data and
+  briefly discusses a special case of priority models, called
+  \emph{maximal progress}.}
+
 %****************************************************************
@@
 \label{secn:components}
-
-%% \noteSBin{%
-%% To guarantee preservation of properties guards and expressions
-%% have to be \emph{monotonic}.  In the case of a trivial order, \ie
-%% when nothing is comparable, \emph{any guard or expression is
-%%   monotonic}.  Thus, this is not really a constraint!
-
-%% Do we put this in the definition of expressions and guards or in
-%% the definitions of components and interaction models?
-%% }
 
@@
   can be used for the interactions with other components (see
-  \defn{im}).  However, in the context of this paper we can simplify
+  \defn{im}).  In the context of this paper, we can simplify
   by omitting this separation.
@@
 
-\begin{definition}[Priority model]
-  \label{defn:priority}
-  A \emph{priority model} over a component interface $(V, P,
-  \export)$\footnote{%
-%
-    Notice that the export function $\export$ has no impact on the
-    priority model definition.
-%
-  } is a strict partial order on interactions: $\pi
-  \subseteq \bigl(2^P \times \guards{V} \times \updates{V} \bigr)^2$.
-
-  We write $\alpha \prec_\pi \beta$, for $(\alpha, \beta) \in \pi$, and 
-   $\filter{\alpha} \bydef{=} \bsetdef{\beta \in (2^P \times
-    \guards{V} \times \updates{V})}{\alpha \prec_\pi \beta}$, for the set of
-  interactions that have higher priority than $\alpha$.
-\end{definition}
-
-\begin{definition}[Application of priority]
-  \label{defn:priority:sem}
-  The application of a priority model $\pi$ over $(V, P, \export)$
-  to a component $B = \tuple{Q, q^0, V, \val{0}{}, P, \export, \goesto{}}$
-  is the component $\pi(B) = \tuple{Q, q^0, V, \val{0}{}, P, \export,
-  \goesto[\pi]{}}$, where $\goesto[\pi]{}$ is the minimal transition
-  relation satisfying the rule (we denote
-  $\filter[q]{\alpha} \bydef{=} %% \filter{\alpha} \cap
-  %% \bsetdef{\beta \in (2^P \times \guards{V} \times \updates{V})}
-  \setdef{\beta \in \filter{\alpha}}{q \goesto{\beta}}$)
-%
-  \begin{equation*}
-    \label{eq:priority:sem}
-%
-    \infer{
-      \alpha = (a, g, u)
-      \and
-      q \goesto{a, g, u} q'
-      \and
-      \textstyle
-      g' = g \land \bigwedge_{(b, h, w) \in \filter[q]{\alpha}} \lnot h
-    }{
-      q \goesto[\pi]{a, g', u} q'
-    }\,.
-  \end{equation*}
-%
-  %% \todoSBin{Add the intuitive explanation}
-\end{definition}
-
-\addSB{Intuitively, an interaction can be fired only if all the
-higher-priority interactions available in the current state are
-disabled by their respective guards.}
-
-In this paper, we will only consider the so-called \emph{maximal
-  progress} priority $\mu$, where $(a, g, u) \prec_\mu (b, h, w)$ iff $a
-\varsubsetneq b$ (\ie $a \subseteq b$ and $a \neq b$).  In
-\secn{conclusion}, we discuss the possibility of generalising the
+\addSB{In addition to interaction models, BIP relies on the so-called
+  \emph{priority models}, imposing a strict partial order on
+  interactions.  Formal definitions are provided in \app{arch:appendix}.  Intuitively, an interaction can be fired only if all
+  the higher-priority interactions available in the current state are
+  disabled by their respective guards.
+%
+In the results and the running example of this paper, we will implicitly assume application of the so-called \emph{maximal
+  progress} priority $\mu$, where $(a, g, u) \prec_\mu (b, h, w)$ iff  $a \subset b$ and $a \neq b$.  For instance, the
+port $\NameTimer.\PortTick$ will never fire alone in a global state,
+where the \noteSB{This turns out to be the first use of the word. I am tempted to pretend I did not notice.}\hl{dangling} port $\PortFail$ is also enabled.
+In \secn{conclusion}, we discuss the possibility of generalising the
 obtained results to other priority models.
-%
-Below, we will assume that the maximal progress priority $\mu$ is
-applied after each composition with an interaction model.
+}
+%% Below, we will assume that the maximal progress priority $\mu$ is
+%% applied after each composition with an interaction model.
 
@@
 %% $a \subset b$ (as sets of ports), $b$ has higher priority than $a$.
-In our running example, under the maximal progress priority, the
-port $\NameTimer.\PortTick$ will never fire alone in a global state,
-where the \noteSB{This turns out to be the first use of the word. I am tempted to pretend I did not notice.}\hl{dangling} port $\PortFail$ is also enabled.
+
+%% In our running example, under the maximal progress priority, the
+%% port $\NameTimer.\PortTick$ will never fire alone in a global state,
+%% where the \noteSB{This turns out to be the first use of the word. I am tempted to pretend I did not notice.}\hl{dangling} port $\PortFail$ is also enabled.
 
@@
 %
-\begin{proof}[Sketch of the proof]
-  %% Commutativity and associativity 
-  Follows from the corresponding
-  properties of set union, Boolean conjunction and
-  semilattice meet.
-%
-%% \todoLH{Check when equivalence is defined}
-%%   Suppose we have two architectures $A \arequiv A'$.  This does not
-%%   necessarily mean that their sets of coordinating components
-%%   coincide.  However, if all the involved coordinating components
-%%   are deterministic, then, in any state of $(A \arcomp A')(\cB)$,
-%%   both architectures will impose the same restrictions, enabling
-%%   the same interactions between the coordinating and operand
-%%   components.  Hence, we have $(A \arcomp A')(\cB) = A(\cB) =
-%%   A'(\cB)$.  Since this holds for any set of components $\cB$, we
-%%   conclude that $A \arcomp A' \arequiv A \arequiv A'$.
+%% \begin{proof}[Sketch of the proof]
+%%   %% Commutativity and associativity 
+%%   Follows from the corresponding
+%%   properties of set union, Boolean conjunction and
+%%   semilattice meet.
 %% %
-%%   The properties of $A_{id}$ follow immediately from the
-%%   definitions of architecture application and composition.
-\end{proof}
+%% %% \todoLH{Check when equivalence is defined}
+%% %%   Suppose we have two architectures $A \arequiv A'$.  This does not
+%% %%   necessarily mean that their sets of coordinating components
+%% %%   coincide.  However, if all the involved coordinating components
+%% %%   are deterministic, then, in any state of $(A \arcomp A')(\cB)$,
+%% %%   both architectures will impose the same restrictions, enabling
+%% %%   the same interactions between the coordinating and operand
+%% %%   components.  Hence, we have $(A \arcomp A')(\cB) = A(\cB) =
+%% %%   A'(\cB)$.  Since this holds for any set of components $\cB$, we
+%% %%   conclude that $A \arcomp A' \arequiv A \arequiv A'$.
+%% %% %
+%% %%   The properties of $A_{id}$ follow immediately from the
+%% %%   definitions of architecture application and composition.
+%% \end{proof}
 
@@
 
-For a component $B$, we denote $S_{\semopen{B}}$,
+For a component $B$, we denote $S_{\semopen{B}}$ and
 $s^0_{\semopen{B}}$ the corresponding constituents of
@@
 \label{property:reset}
-\addSB{Although we define properties as state predicates, any
+Although we define properties as state predicates, any
 appropriate logic can be used to specify them.  For instance, the
-  property \emph{``There is always a possibility to reset the system
-    or resume operation after a single failure'' (\ie without
-    additional failures occuring in the meantime)} enforced by the
-  Failure Monitor architecture can be specified using CTL as $\AG
-  \bigl(\PortFail \rightarrow \EU[]{\lnot \PortFail}{(\PortResume \lor
-    \PortReset)}\bigr)$.  Additional properties are provided in
-  \app{properties}.}
+property \addSB{\emph{``There is always a possibility to reset the system
+  after a single failure''} (\ie without
+  additional failures having to occur in the meantime)} enforced by the
+Failure Monitor architecture can be specified using CTL as \noteSB{Removed $\lnot \PortResume$, because not needed \emph{and} could not reformulate nicely in English.}\addSB{$\AG
+\bigl(\PortFail \rightarrow \EX \EU[]{\lnot \PortFail}{
+  \PortReset}\bigr)$}.  Additional properties are provided in
+\app{properties}.
 
@@
 
-\defn{up:compat} in \secn{arch:appendix} provides a formal definition
-of the notion of \emph{upwards compatibility}, which we present here
+\defn{up:compat} in \app{arch:appendix} provides a formal definition
+of the notion of \emph{upwards compatibility} needed to ensure property preservation when composing architectures relying on the maximal progress priority model.  Here, we present it
 informally due to page limitations.  Two architectures $A_1$ and $A_2$
@@
 
+This section provides the formal definitions related to priority
+models, which are omitted from the main body of the paper due to size
+limitations.
+
+\begin{definition}[Priority model]
+  \label{defn:priority}
+  A \emph{priority model} over a component interface $(V, P,
+  \export)$\footnote{%
+%
+    Notice that the export function $\export$ has no impact on the
+    priority model definition.
+%
+  } is a strict partial order on interactions: $\pi
+  \subseteq \bigl(2^P \times \guards{V} \times \updates{V} \bigr)^2$.
+
+  We write $\alpha \prec_\pi \beta$, for $(\alpha, \beta) \in \pi$, and 
+   $\filter{\alpha} \bydef{=} \bsetdef{\beta \in (2^P \times
+    \guards{V} \times \updates{V})}{\alpha \prec_\pi \beta}$, for the set of
+  interactions that have higher priority than $\alpha$.
+\end{definition}
+
+\begin{definition}[Application of priority]
+  \label{defn:priority:sem}
+  The application of a priority model $\pi$ over $(V, P, \export)$
+  to a component $B = \tuple{Q, q^0, V, \val{0}{}, P, \export, \goesto{}}$
+  is the component $\pi(B) = \tuple{Q, q^0, V, \val{0}{}, P, \export,
+  \goesto[\pi]{}}$, where $\goesto[\pi]{}$ is the minimal transition
+  relation satisfying the rule (we denote
+  $\filter[q]{\alpha} \bydef{=} %% \filter{\alpha} \cap
+  %% \bsetdef{\beta \in (2^P \times \guards{V} \times \updates{V})}
+  \setdef{\beta \in \filter{\alpha}}{q \goesto{\beta}}$)
+%
+  \begin{equation*}
+    \label{eq:priority:sem}
+%
+    \infer{
+      \alpha = (a, g, u)
+      \and
+      q \goesto{a, g, u} q'
+      \and
+      \textstyle
+      g' = g \land \bigwedge_{(b, h, w) \in \filter[q]{\alpha}} \lnot h
+    }{
+      q \goesto[\pi]{a, g', u} q'
+    }\,.
+  \end{equation*}
+%
+  %% \todoSBin{Add the intuitive explanation}
+\end{definition}
+
 \begin{definition}[Upwards compatibility]
   \label{defn:up:compat}
-  \todoSB{Summarise in English and move to the appendix}
-%
   Consider two architectures $A_i = \tuple{\cC_i, V_{A_i}, P_{A_i},
@@
 \begin{enumerate}
-\item There is always a possibility to reset the system or resume
-  operation after a single failure (\ie without additional failures
-  occuring in the meantime):
+\item There is always a possibility to reset the system
+  after a single failure (\ie without additional failures
+  having to occur in the meantime):
   \begin{equation}
     \label{eq:prop:reset:can}
-    \AG \bigl(\PortFail \rightarrow \EU[]{\lnot \PortFail}{(\PortResume \lor \PortReset)}\bigr).
+    \AG \bigl(\PortFail \rightarrow \EX \EU[]{\lnot \PortFail}{\PortReset}\bigr).
   \end{equation}

### 2019-02-14 2016-Weak-FH-Bisim/WeakBisim.tex
corrections

@@
  \end{mathpar}
-So we need to prove that the following holds:\\
+So we need to prove that the following statement holds:\\
 $\Pred_{s,t} \land \Pred\\
@@
      \Pred_{s_1^1,t_x}\subst{\Post^1}\subst{\Post_{OT_x}}\right)$\\
-The conjunction with the term $\Pred^2\subst{\Post^1}$ of the both sides of the implication, we get:\\  
+The conjunction of the term $\Pred^2\subst{\Post^1}$ with the both sides of the implication, we get:\\  
 $(\Pred_{s,t} \land \Pred^1)\wedge\Pred^2\subst{\Post^1}\\
@@
 
-$\forall p \in [0..(n_1+n_2+2)]\,\, Q\models{\openrule
+$\forall p \in [0..(n_1\!+\!n_2\!+\!2)]\,\, Q\models{\openrule
 			{
@@
 We can decompose each of the $n$ subsequences; the length of the subsequence number $k$ is $n_k$,  and the subsequence is made of the following OTs:\\
-$\forall p\! \in\! [0..(n'-1)] Q\models{\openrule
+$\forall p\! \in\! [0..(n_k'\!-\!1)] Q\models{\openrule
 			{
@@
 				{{\Post^{2b}}}}
-				{\ostate{v_{n'l}^{l\in L_Q}} \OTarrow {\alpha'_k}
-				\ostate{v_{(n'+1)l}^{l\in L_Q}}}
+				{\ostate{v_{n_k'l}^{l\in L_Q}} \OTarrow {\alpha'_k}
+				\ostate{v_{(n_k'+1)l}^{l\in L_Q}}}
 				}%\]
@@
 and
-$\forall p \in [(n'+1)..(n_k-1)]\,\, Q\models{\openrule
+$\forall p \in [(n_k'\!+\!1)..(n_k\!-\!1)]\,\, Q\models{\openrule
 			{
@@
 $\forall j \in  (J\cap\Holes(Q)),\,
-\displaystyle{\gamma'_{kj} }=\mybigdotcup_{i=0}^{(n'-1)}\!\!\vis{\beta^1_{ij}}\,\dotcup\,\vis{\set{\beta^2_j}}\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij}}
+\displaystyle{\gamma'_{kj} }=\mybigdotcup_{i=0}^{(n_k'-1)}\!\!\vis{\beta^1_{ij}}\,\dotcup\,\vis{\set{\beta^2_j}}\,\dotcup\!\!\!\mybigdotcup_{i=(n_k'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij}}
 \\
-\Pred^b_k=\Big(\!\!\!\bigwedge_{i=0}^{(n'-1)}\!\!
+\Pred^b_k=\Big(\!\!\!\bigwedge_{i=0}^{(n_k'-1)}\!\!
 {\Pred_i^{1b}}\bigotimes_{j=0}^{(i-1)}\subst{{\Post_j^{1b}}}\Big)
-\land\Big({\Pred^{2b}}\bigotimes_{i=0}^{(n'-1)}\subst{{\Post_i^{1b}}}\Big)\land\\
-~\qquad\qquad\Big(\!\!\!\bigwedge_{i=(n'+1)}^{(n_k-1)}\!\!\!{\Pred_i^{3b}}\bigotimes_{j=n'+1}^{(i-1)}\subst{{\Post_j^{3b}}}\subst{{\Post^{2b}}}\bigotimes_{i=0}^{(n'-1)}\subst{{\Post_i^{1b}}}\Big)\\
-\Post^b_k=\bigotimes_{i=(n'+1)}^{(n_k-1)}\!\!\!{\Post_i^{3b}}\Big(\subst{{\Post^{2b}}}\bigotimes_{i=0}^{(n'-1)}\subst{{\Post_i^{1b}}}\Big)
+\land\Big({\Pred^{2b}}\bigotimes_{i=0}^{(n_k'-1)}\subst{{\Post_i^{1b}}}\Big)\land\\
+~\qquad\qquad\Big(\!\!\!\bigwedge_{i=(n_k'+1)}^{(n_k-1)}\!\!\!{\Pred_i^{3b}}\bigotimes_{j=n_k'+1}^{(i-1)}\subst{{\Post_j^{3b}}}\subst{{\Post^{2b}}}\bigotimes_{i=0}^{(n_k'-1)}\subst{{\Post_i^{1b}}}\Big)\\
+\Post^b_k=\bigotimes_{i=(n_k'+1)}^{(n_k-1)}\!\!\!{\Post_i^{3b}}\Big(\subst{{\Post^{2b}}}\bigotimes_{i=0}^{(n_k'-1)}\subst{{\Post_i^{1b}}}\Big)
 $\\
@@
 $\displaystyle{\gamma_{j_0}}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{i{j_0}}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{i{j_0}}}=[\alpha'_0..
-\alpha'_n]$, indeed $\displaystyle{\gamma_{j_0}}$ is a a list of $\alpha_p$ such that $p\in [0..n_1+n_2+1] \land \alpha_p\neq \tau$.
+\alpha'_n]$, indeed $\displaystyle{\gamma_{j_0}}$ is a a list of $\alpha_p$ such that $p\in [0..(n_1\!+\!n_2\!+\!1)] \land \alpha_p\neq \tau$.
 %$\displaystyle{\gamma_{kj_0} }=\mybigdotcup_{i=0}^{(n'-1)}\!\!\vis{\beta^1_{ij_0}}\,\dotcup\,\vis{\set{\beta^2_{j_0}}}\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij_0}}$ \TODO{?????}\\

### 2019-02-14 2018-Arch-pNets/arch-pNets.tex
First pass ; shortening sec 3

@@
   \and
-	Univ Lyon, CNRS, ENS de Lyon, Inria, Universit\'e Claude Bernard Lyon 1, LIP, Lyon, France -- \email{ludovic.henrio@ens-lyon.fr}
+	Univ Lyon, EnsL, UCBL, CNRS, Inria,  LIP, F-69342, LYON Cedex 07, France\\ \email{ludovic.henrio@ens-lyon.fr}
   \and
@@
 	\label{defn:open-automaton}
-	An \emph{open automaton} is a structure\\ $A =
-	<J,\mathcal{S},s_0,\mathcal{T}>$ where:
-	\begin{itemize}
-		\item   $J$ is a  set of indices,
-		\item   $\mathcal{S}$ is a set of states and $s_0$ an initial state
+	An \emph{open automaton} is a tuple $<\!\!J,\mathcal{S},s_0,\mathcal{T}\!\!>$ where:
+%	\begin{itemize}
+%		\item  
+ $J$ is a  set of indices,
+%		\item 
+  $\mathcal{S}$ is a set of states and $s_0$ an initial state
 		among $\mathcal{S}$,
-		\item $\mathcal{T}$ is a set of open transitions and for each
+%		\item 
+$\mathcal{T}$ is a set of open transitions and for each
 		$t\in \mathcal{T}$ there exist  $J'$ with  $J'
@@
 		and  $\mathcal{S}$.
-
-	\end{itemize}
+%		
+%	\end{itemize}
 \end{definition}
@@
 tuples of states of the pLTSs at the leaves. We denote them $\triangleleft\ldots\triangleright$ for distinguishing tuple 
-states from other tuples. given by 
-Definition~\ref{def-states}. 
-The open transitions first
+states from other tuples. 
+%given by 
+%Definition~\ref{def-states}. 
+An open transition first
  project the global state into states of the leaves, then apply
-pLTS transitions on these states, and compose them with the sort of the holes according to the synchronisation defined in the synchronisation vectors.
-More precisely, each open transition between two states is defined as a composition of transition from some pLTSs and actions of some holes as follows: 1) the actions of the holes involved in the transition, 2) a guard  built from the synchronisation vectors coordinating the holes and the transitions involved; 3) assignments defined by the pLTSs transitions involved.
+pLTS transitions on these states, and compose them with the actions of the holes according to the synchronisation vectors.
+More precisely, each open transition between two states is defined as a composition of transition from some pLTSs and actions of some holes as follows: 1) the actions of the holes involved in the transition, 2) a guard  built from the synchronisation vectors coordinating the holes and the transitions involved; 3) assignments and global state change are defined by the pLTSs transitions involved.
 The synchronisation vectors also define the global action.
-The global state evolution is also defined by the set of state transitions of the pLTSs involved in the pLTSs.
 
@@
 
-\addSB{This section presents the extension of the theory of
+This section presents the extension of the theory of
   architectures \cite{AttieBBJS16-architectures-faoc} with data and
   briefly discusses a special case of priority models, called
-  \emph{maximal progress}.}
+  \emph{maximal progress}.
 
@@
 \label{secn:components}
-
-\begin{definition}[Components]
+\begin{definition}[Component]
   \label{defn:component}
-  A \emph{component} is a tuple $\tuple{Q, q^0, V, \val{0}{}, P,
-  \export, \goesto{}}$, where
+  A component is a tuple $\tuple{Q, q^0, V, \val{0}{}, P,
+  \export, \goesto{}}$ where\\[-4ex]
   \begin{itemize}
@@
     valuation} of the component variables, 
-  \item $P$ is a set of \emph{ports}, with
-    $\export : P \rightarrow 2^V$ 
+  \item $P$ is a set of \emph{ports};
+    $\export : P \rightarrow 2^V$ is
     the \emph{set of variables exported by each port},
@@
   We call the triple $(V,P, \export)$ the \emph{interface} of the
-  component.\,\footnote{%
-%
-  In practice, only exported variables, \ie those in the set
-  $\bigcup_{p \in P}\export(p)$, belong to the component interface and
-  can be used for the interactions with other components (see
-  \defn{im}).  In the context of this paper, we can simplify
-  by omitting this separation.
-%
+  component.\,\footnote{Only exported variables, belonging to a
+  $\export(p)$, appear in the component interface  (see
+  \defn{im}).  We omit here this separation between internal and exported variables.
   }
@@
 
-In this paper, we will use a running example, which is a refined
+In this paper, we  use  a refined
 version of the Failure Monitor architecture
-from~\cite{CubETH-case-study}.  Although \fig{schema:ArchFailure:BIP}
+from~\cite{CubETH-case-study} as a running example.  Although \fig{schema:ArchFailure:BIP}
 shows the full definition of this architecture, we will explain its
-various elements progressively, as we define the corresponding
-notions.
-
-The model in \fig{schema:ArchFailure:BIP} has  components
+various elements progressively.
+\fig{schema:ArchFailure:BIP} shows  components
 %% The
@@
   \{\PortTick, \PortCancel, \PortTOT\},
-  \bigl\{\PortTick \mapsto \{t, z\}\bigr\}
+  \bigl\{\!\PortTick \mapsto \{t, z\}\!\bigr\}
 }$,
@@
   \{\PortReset, \PortFail, \PortResume, \PortTOC\},
-  \bigl\{\PortFail \mapsto \{\mathit{zone}\}\bigr\}
-}$, respectively.
+  \bigl\{\!\PortFail \mapsto \{\mathit{zone}\}\!\bigr\}
+}$ respectively.
 %
@@
 Variable $t$ is implicitly assumed to be an integer.  Variables $z$
-and $\mathit{zone}$ are implicitly assumed to be integer intervals of
-the form $[l,u]$.  For both types, we also implicitly assume the
+and $\mathit{zone}$ are  integer intervals of
+the form $[l,u]$.  Both types are implicitly equipped with a
 natural ordering: increasing integers and interval inclusion.
@@
 variables.  \Eg[,] the loop transition $\tstate{0}
-\goesto{\PortTick, \GuardTick[], \TimerUpd[]} \tstate{0}$ in the
-component $\NameTimer$ is labeled by the port $\PortTick$.  It can be
-fired only when the current value of the local variable $t$ is less
-than $z.u$.
-%% , where $z = [l, u]$ is a local variable representing an
-%% interval
-Upon firing, this transition increments the value of $t$ by $1$.  The
+\goesto{\PortTick, \GuardTick[], \TimerUpd[]} \tstate{0}$. % in the
+%component $\NameTimer$ is labeled by the port $\PortTick$, the associated guarg and variable update. 
+% It can be
+%fired only when the current value of the local variable $t$ is less
+%than $z.u$.
+%%% , where $z = [l, u]$ is a local variable representing an
+%%% interval
+%Upon firing, this transition increments the value of $t$ by $1$.  
+The
 guards and update assignments of the transitions of $\NameCtrl$ are
-omitted.  The default values are the constant predicate $\true$ (true) and
-the empty assignment {\noop}, respectively.  
+omitted. By default, an omitted guard is  $\true$ (true) and an omitted assignment is empty {\noop}.  
 %\noteLH{It looks like Max is in zone, I do not understand}
@@
 fourth premise in \eq{comp:semantics} restricts the set of
-variables, which can be affected by such data transfer, to those
+variables that can be affected by such data transfer to those
 that are exported through the ports participating in the
@@
   for any interaction $(a, g, u) \in \Gamma$, we have
-  $g \in \guards{\export(a)}$ and $e \in \updates{\export(a)}$.\footnote{%
+  $g \in \guards{\export(a)}$ and $u \in \updates{\export(a)}$.\footnote{%
 %
@@
 %% \noteLH{supp should go outside the definition}
-When speaking of a set of components or interfaces, we will always
-assume that it satisfies the disjointness assumption of \defn{im}.
+We  
+assume that all sets of components and interfaces satisfy the disjointness assumption above.
 %
 We call the \emph{support} of a set of ports $a \subseteq P$, denoted
-$\supp{a}$, either the set $\setdef{i \in I}{a \cap P_i \neq
+$\supp{a}$, the set of the participating components. It is either the set $\setdef{i \in I}{a \cap P_i \neq
   \emptyset}$ (for $P = \bigcup_{i=1}^n P_i$) or the set $\setdef{B
@@
 P_B$).  The precise meaning of this notation will always be clear from
-the context.  Intuitively, for an interaction $(a, g, u)$, $\supp{a}$
-denotes the set of the participating components.
+the context.
 
@@
   q^0_i, V_i, \val{0}{i}, P_i, \export[i], \goesto{}}^{i \in I}$ with
-  the interaction model $\Gamma$ over $\tuple{V, P, \export}$ (as in \defn{im})
+  the interaction model $\Gamma$ over $\tuple{V, P, \export}$
   is the component $\Gamma(\cB) = \tuple{Q, q^0, V, \val{0}{}, P,
@@
 structure interactions in BIP models.
-
 Connectors are hierarchical, tree-like structures with component ports
@@
 The interaction model is defined as the set of all interactions
-allowed by at least one of the connectors in the system.
+allowed by at least one of the connectors.
 %% The composition semantics of BIP systems consists in
@@
 For instance, the connector {\NameTimer.\PortTick
-  \trigsynch (\PortFail \trigsynch \NameCtrl.\PortFail)} is a
-two-level hierarchical connector.  In the second-level subconnector
+  \trigsynch (\PortFail \trigsynch \NameCtrl.\PortFail)} of \fig{schema:ArchFailure:BIP} is a
+two-level hierarchical connector.  In the  subconnector
 {\PortFail \trigsynch \NameCtrl.\PortFail}, the port {\PortFail} is a
-trigger, whereas {\NameCtrl.\PortFail} is a synchron.  Therefore, this
-subconnector allows two interactions labelled $\{\PortFail\}$ and $\listset{\NameCtrl.\PortFail, \PortFail}$.  Similarly, at the top level,
-{\NameTimer.\PortTick} is a trigger, whereas the second-level
-subconnector is a synchron.  Hence, the overall connector allows the
-interaction involving only one port {\NameTimer.\PortTick}\footnote{%
-%
-  Such interactions are called \emph{singleton interactions}.
-%
-} and any interaction involving both {\NameTimer.\PortTick} and
-\emph{some} interaction of the second-level subconnector.  Combining
-the two levels we can see that the entire connector defines the
+trigger, whereas {\NameCtrl.\PortFail} is a synchron.  This
+subconnector allows two interactions: $\{\PortFail\}$ and $\listset{\NameCtrl.\PortFail, \PortFail}$.  Similarly, at the top level,
+{\NameTimer.\PortTick} is a trigger, and the 
+subconnector is a synchron. 
+% Hence, the overall connector allows the
+%interaction involving only one port {\NameTimer.\PortTick}\footnote{%
+%%
+%  Such interactions are called \emph{singleton interactions}.
+%%
+%} and any interaction involving both {\NameTimer.\PortTick} and
+%\emph{some} interaction of the second-level subconnector.  
+%Combining
+%the two levels we can see that t
+The entire connector defines the
 following three interactions (observe that $\topinterval +
@@
 %
-\begin{gather*}
-  \bigl(\{\NameTimer.\PortTick\},
+%\begin{gather*}
+$  \bigl(\{\NameTimer.\PortTick\},
   \true, \emptyset\bigr)
   %% \NameTimer.z := \NameTimer.z\bigr)
-  ,
-%
-  \qquad
-%
-  \bigl(\{\PortFail, \NameTimer.\PortTick\},
-  \true, \emptyset\bigr)
+ $,
+$  \bigl(\{\PortFail, \NameTimer.\PortTick\},
+  \true, \emptyset\bigr)$
   %% \NameTimer.z := \NameTimer.z\bigr)
   ,
-%
-  \\
-%
+$
   \bigl(\{\NameCtrl.\PortFail, \PortFail, \NameTimer.\PortTick \},
@@
   \NameTimer.z := \NameTimer.z \cap (\NameCtrl.\mathit{zone} + \NameTimer.t)\bigr)
-  .
-\end{gather*}
+$
+%  .
+%\end{gather*}
 %% \begin{align*}
@@
 
-\addSB{In addition to interaction models, BIP relies on the so-called
-  \emph{priority models}, imposing a strict partial order on
+\addSB{In addition to interaction models, BIP relies on 
+  \emph{priority models} that impose  a strict partial order on
   interactions.  Formal definitions are provided in \app{arch:appendix}.  Intuitively, an interaction can be fired only if all
@@
 %
-In the results and the running example of this paper, we will implicitly assume application of the so-called \emph{maximal
+In the next sections, we will implicitly assume application of the  \emph{maximal
   progress} priority $\mu$, where $(a, g, u) \prec_\mu (b, h, w)$ iff  $a \subset b$ and $a \neq b$.  For instance, the
-port $\NameTimer.\PortTick$ will never fire alone in a global state,
-where the \noteSB{This turns out to be the first use of the word. I am tempted to pretend I did not notice.}\hl{dangling} port $\PortFail$ is also enabled.
-In \secn{conclusion}, we discuss the possibility of generalising the
+port $\NameTimer.\PortTick$ will never fire alone if the port $\PortFail$ is also enabled.
+In \secn{conclusion}, we discuss the generalisation of the
 obtained results to other priority models.
@@
 
-Architectures are partially defined BIP models, where \emph{dangling}
-ports serve as placeholders for the eventual connection with
-additional \emph{operand} components.
+Architectures are partial BIP models, with \emph{dangling}
+ports that serve as placeholders for the eventual connection with
+ \emph{operand} components.
 
@@
 %
-  and $\mu$ is the maximal progress priority model.
+  and $\mu(...)$ denotes the application of the maximal progress priority model.
 \end{definition}
@@
 interaction.  %% In particular, they can join the interactions in
-%% $\Gamma$ (see \eq{im:extension}).  If the interface of the
+%% $\Gamma$ (see \defn{arch:application}).  If the interface of the
 %% architecture covers all ports of the system, \ie $P = P_A$, we
@@
 
-Below, for the sake of clarity, we start by presenting in
-\secn{enc:nopri} the encoding of $A$ into pNets without accounting for
-any priority model (see \secn{components}).  Then, in
-\secn{enc:maxprog}, we slightly modify this encoding to include the
-implicitly assumed maximal progress priority.
-
-%****************************************************************
-\subsection{Encoding without the priority model}
-\label{secn:enc:nopri}
+For the sake of clarity and conciseness, we define the encoding of $A$
+into pNets without accounting for any priority model (see
+\secn{components}).  Then, we provide a brief sketch of the
+modification necessary to incorporate the implicitly assumed maximal
+progress priority.
+
+%% %****************************************************************
+%% \subsection{Encoding without the priority model}
+%% \label{secn:enc:nopri}
 
@@
 by the initial valuation $\val{0}{C}$ of $C$, 2)~define a pNet action algebra that associates, as action parameter, an
-additional Boolean value to each port, \add{3)~for each exported variable $x$, create the corresponding fresh variable $x'$ to allow updates during interactions,} 4)~create pNet transitions that reflect the original transitions of
+additional Boolean value to each port, \add{3)~for each exported variable $x$, create the corresponding fresh variable $?x'$ to allow updates during interactions,} 4)~create pNet transitions that reflect the original transitions of
 $C$ with $\true$ as parameter and 5)~create additional loop transitions marked by
@@
 \item $s_0 \not\in Q_C$ is fresh and $S = Q_C \cup \{s_0\}$,
-\item $\vars(s) = V_C \cup \setdef{x'}{x \in \export[C](p), p \in a, s\goesto{a} }$, for all $s \in Q_C$, and $\vars(s_0) =
+\item $\vars(s) = V_C \cup \setdef{?x'}{x \in \export[C](p), p \in a, s\goesto{a} }$, for all $s \in Q_C$, and $\vars(s_0) =
   \emptyset$,
@@
 
-\item denoting  $\mathit{init} \bydef{=} \bigl(x := \val{0}{C}(x)\bigr)^{x \in V_C}$;
+\item denoting  $\mathit{init} \bydef{=} \bigl(x := \val{0}{C}(x)\bigr)^{x \in V_C}$ and,
   \noteSB{Ludo, Eric, pourriez-vous v\'erifier que cela est compr\'ehensible ?}%
@@
   \cup
-  \bigl(x := e_x\bigl[\nicefrac{x'}{x}\bigr]\bigr)^{x \in V \cap \export[C](a)}$,
-%
-  and $\export[C]'(a) \bydef{=} \setdef{x'}{x \in \export[C](p), p \in a}$,
+  \bigl(x := e_x\bigl[\nicefrac{?x'}{x}\bigr]\bigr)^{x \in V \cap \export[C](a)}$,
+%
+  and $\export[C]'(a) \bydef{=} \setdef{?x'}{x \in \export[C](p), p \in a}$,
 %
@@
 have an associated Boolean value, nor the additional loop transitions.
-\todoSB{Revise this if necessary}\hl{We will explicitate this optimisation after we define the
-encoding of the interaction model.}
+We will explain this optimisation after we define the
+encoding of the interaction model.
 
@@
 
-\todoSB{Update?}\hl{In order to encode these interactions using only one synchronisation vector}, we use
+\addSB{We encode all interactions of a connector in one synchronisation vector.  This will allow us to also encode the maximal progress priority model.}
+We use
 the additional Boolean values associated to each port by the encoding
@@
 form a ``causality chain'': {\NameCtrl.\PortFail} can only
-participate in the interaction if the dangling port {\PortFail}
-participates, which in turn can only participate if
+participate in an interaction if the dangling port {\PortFail}
+participates, which in turn can only happen if
 {\NameTimer.\PortTick} does so.  These dependencies can be rewritten
@@
 
-However, notice
-that, within the scope of this connector, {\NameTimer.\PortTick}
-participates in all the interactions.
-%
-Furthermore, {\NameTimer.\PortTick} is not involved in any other
-connector.  Therefore, the loop transition in \nopri[\NameTimer]
-labelled by $\PortTick(\false)$ can never be taken and, therefore can
-be removed from the encoding.  Furthermore, since only the transition
+Within the scope of this connector, the port {\NameTimer.\PortTick}
+participates in all interactions.
+%
+Furthermore, it is not involved in any other
+connector.  Hence, the loop transition in \nopri[\NameTimer]
+labelled by $\PortTick(\false)$ can never be taken and, therefore, can
+be removed from the encoding.  Since only the transition
 labelled by $\PortTick(\true)$ is ever taken, 
@@
 We obtain the
-synchronisation vector SV0 shown in \fig{FailureTimer:pNet}, where $b_0$ and
-$b_1$ are the Boolean values associated to the actions encoding the
-ports {\PortFail} and {\NameCtrl.\PortFail}, $\alpha_0$ is a fresh
-action name.  The guard $b_1 \Rightarrow b_0$ encodes the causal
+synchronisation vector SV0 shown in \fig{FailureTimer:pNet}, where $b0$ and
+$b1$ are the Boolean values associated to the actions encoding the
+ports {\PortFail} and {\NameCtrl.\PortFail}.
+The guard $b_1 \Rightarrow b_0$ encodes the causal
 relation between ports {\NameCtrl.\PortFail} and {\PortFail}.  Notice
@@
 
+\addSB{In the general encoding, the global actions of the
+  synchronisation vectors should be fresh action names.  However, for
+  the properties considered in our case study, we only need to exhibit
+  the actions of the holes.  Furthermore, each synchronisation vector
+  involves at most one such action.  This allows us to reuse them as
+  the global actions of the synchronisation vectors, simplifying the
+  translation of properties to be verified (\cf \secn{arch:verif}).}
+
 The general case encoding relies on the causal semantics of the
@@
 the Algebra of Causal Interaction Trees $\ct(P)$, explicitates the
-causal dependencies discussed above, through an encoding mapping
+causal dependencies discussed above through an encoding mapping
 $\tau: \ac(P) \rightarrow \ct(P)$.  Another mapping $R: \ct(P)
@@
 the update assignement
-\[
+$
 \NameTimer.\mathit{z} := \NameTimer.\mathit{z}
-\cap \Big(
-\bigl(
+\cap \bigl(
+(
 \NameCtrl.\PortFail\ ?\ \NameCtrl.\mathit{zone} : \topinterval
-\bigr)
-+ \NameTimer.\mathit{t} \Big)
-\]
+)
++ \NameTimer.\mathit{t} \bigr)
+$
 associated to the connector {\NameTimer.\PortTick \trigsynch
@@
   \nopri[x,g,u] \bydef{=}
-  \Tuple{p\bigl(\export[A](p),{{\color{blue}\export[A]'(p),}}b_p\bigr)}^{p \in P_x}
+  %% \Tuple{p\bigl(\export[A](p),{{\color{blue}\export[A]'(p),}}b_p\bigr)}^{p \in P_x}
+  \Tuple{\Setdef{p\bigl(\export[A](p),\export[A]'(p),b_p\bigr)}{p \in P_x \cap P}}^{P \in P_C^{C \in \cC} \cup \partition}
   \rightarrow
@@
     \bigwedge R(\tau(x))\bigl[\nicefrac{b_p}{p}\bigr]
-    {\color{blue}{}
     \land
-    \bigwedge_{(x := e_x) \in u} (x' = e_x)
+    \bigwedge_{(x := e_x) \in u} (?x' = e_x)
     \land
-    \bigwedge_{x \in \export[A](x), x \not\in u} (x' = x)
-    }
+    \bigwedge_{x \in \export[A](x), x \not\in u} (?x' = x)
     \right]
@@
 \end{multline}
-\noteSB{Ought to group ports by components in
-  $\Tuple{p\bigl(\export[A](p),\export[A]'(p),b_p\bigr)}^{p \in P_x}$...
-  \newline
-  Will probably restrict interactions to one port per component
-  throughout the paper to simplify.
-}
+%% \noteSB{Ought to group ports by components in
+%%   $\Tuple{p\bigl(\export[A](p),\export[A]'(p),b_p\bigr)}^{p \in P_x}$...
+%%   \newline
+%%   Will probably restrict interactions to one port per component
+%%   throughout the paper to simplify.
+%% }
 %
@@
 illustrated in \tab{connectors}, $\bigl[\nicefrac{b_p}{p}\bigr]$ is
-the substitution, which replaces, in the expression that preceeds it,
+the substitution that replaces in the expression that preceeds it
 all occurrences of $p$ by $b_p$.
@@
   isomorphic to the LTS $\semopen{\Gamma\bigl(\cC_A, (B_D)^{D \in
-      \partition}\bigr)}$ (see \defn{comp:semantics}), where, for each
+      \partition}\bigr)}$ (see \defn{comp:semantics}), with, for each
   $D \in \partition$, the component $B_D \bydef{=} \tuple{\{q\}, q,
@@
   a fresh state $q$ and
-
 %
@@
 %
-\begin{proof}[Sketch of a proof]
-  \noteSB{This theorem is very probably correct: the key question is
-  whether isomorphism is, indeed, the relation to use. In absence of
-  silent transitions, must be the case.}
-  The theorem follows from the correctness of $\tau$ and $R$ shown in
-  \cite{BliSif10-causal-fmsd}.
-\end{proof}
-
-\todoSB{This repeats things that were already said before.  Will reduce.}
-Observe now that this encoding can be optimised to remove unnecessary
-Boolean variables and loop transitions marked by \false.  For
-instance, consider the ports shown in red in the second column of
-\tab{connectors}.  All these ports only appear in the roots of the
-corresponding causal interaction trees and, furthermore, each of these
-trees only has one root (see \app{trees}).  In such cases, as in the
-{\NameTimer.\PortTick \trigsynch (\PortFail \trigsynch
-  \NameCtrl.\PortFail)} example discussed above, the Boolean variables
-and the \false-marked loop transitions associated to these ports can
-be removed.  Furthermore, the rules associated to these ports in the
-corresponding systems of causal rules (see the rules in red in the
-third column of \tab{connectors}) become tautological and can also be
-removed from the corresponding guards in \eq{nopri:connector}.
-
-%****************************************************************
-\subsection{Encoding with the maximal progress priority model}
-\label{secn:enc:maxprog}
-
-\noteSBin{In order to encode the maximal progress priority model, one
-  has to introduce an additional Boolean variable, for each port (for
-  which we have introduced one in $\nopri[A, \partition]$), such that
-  $q \goesto{p(b_p, \true)} q'$ iff $\exists q'': q \goesto{p(\true)}
-  q''$ in $\nopri[A, \partition]$.  Intuitively, this variable
-  indicates whether \emph{there is a possibility to fire $p$ from the
-    same state}.  Then, in the SV guard, we have to check whether
-  \emph{all ports in $c_p(\tau(x))$ can be fired} (see
+%% \begin{proof}[Sketch of a proof]
+%%   \noteSB{This theorem is very probably correct: the key question is
+%%   whether isomorphism is, indeed, the relation to use. In absence of
+%%   silent transitions, must be the case.}
+%%   The theorem follows from the correctness of $\tau$ and $R$ shown in
+%%   \cite{BliSif10-causal-fmsd}.
+%% \end{proof}
+
+%% \todoSB{This repeats things that were already said before.  Will reduce.}
+%% Observe now that this encoding can be optimised to remove unnecessary
+%% Boolean variables and loop transitions marked by \false.  For
+%% instance, consider the ports shown in red in the second column of
+%% \tab{connectors}.  All these ports only appear in the roots of the
+%% corresponding causal interaction trees and, furthermore, each of these
+%% trees only has one root (see \app{trees}).  In such cases, as in the
+%% {\NameTimer.\PortTick \trigsynch (\PortFail \trigsynch
+%%   \NameCtrl.\PortFail)} example discussed above, the Boolean variables
+%% and the \false-marked loop transitions associated to these ports can
+%% be removed.  Furthermore, the rules associated to these ports in the
+%% corresponding systems of causal rules (see the rules in red in the
+%% third column of \tab{connectors}) become tautological and can also be
+%% removed from the corresponding guards in \eq{nopri:connector}.
+
+%% %****************************************************************
+%% \subsection{Encoding with the maximal progress priority model}
+%% \label{secn:enc:maxprog}
+
+\bigskip
+In order to encode the maximal progress priority model, one has to
+introduce an additional Boolean variable, for each port, for which we
+have introduced one in $\nopri[A, \partition]$.  Intuitively, the
+variables introduced above determine whether the original transition
+labeled by the port is executed (\true), or rather the corresponding
+self-loop, introduced by the encoding (\false).  The new variables
+determine whether \emph{there is an original transition labelled by
+  $p$ that could be executed from the same state}, \ie[,] with $b_p$
+the variable introduced above for the encoding without maximal
+progress, $q \goesto{p(\true, b_p)} q'$ iff $\exists q'': q
+\goesto{p(b_p)} q''$ with $b_p = \true$ in $\nopri[A, \partition]$.
+Then, in the SV guard, we have to check whether \emph{all ports
+  leading to $p$ in the caual tree $\tau(x)$ can be fired} (see
 \app{transformations}).  If so, then $p$ must be fired, \ie
-  $p(\false)$ must be blocked.  This is pretty much straightforward,
-  but care must be taken when doing this in the general case, since
-  causal interaction trees can get pretty tricky due to $\oplus$ (see
-  \app{trees}).}
+$p(\false)$ must be blocked.  %% This is pretty much straightforward, but
+%% care must be taken when doing this in the general case, since causal
+%% interaction trees can get pretty tricky due to $\oplus$ (see
+%% \app{trees}).}
 %****************************************************************
@@
   Consider $(a,g,e) \in \IMextend{\Gamma}{P}$.  By
-  \eq{im:extension}, this is equivalent to
+  \defn{arch:application}, this is equivalent to
   $(a \cap P_A, g, e) \in \Gamma$.
@@
   \val{}{})$, such that $a \cap P_2 \subseteq b_2$ and $b_2 \cap P_1 =
-  b_1 \cap P_2$.  By \eq{im:extension}, we have $(b_1 \cap P_{A_1},
+  b_1 \cap P_2$.  By \defn{arch:application}, we have $(b_1 \cap P_{A_1},
   h^1, e^1) \in \Gamma^1$.  Furthermore,
@@
   P_{A_1}) \cup (b_2 \cap P_{A_2}), h^1 \land h^2, f^1 \expmix f^2)
-  \in \Gamma$ and, by \eq{im:extension}, $(b_1 \cup b_2, h^1 \land
+  \in \Gamma$ and, by \defn{arch:application}, $(b_1 \cup b_2, h^1 \land
   h^2, f^1 \expmix f^2) \in \IMextend{\Gamma}{(P_1 \cup P_2)}$.
@@
 
-  In particular, the first safety property:
-  \begin{equation}*
-    \label{eq:prop:reset:can}
+  In particular, the first safety property \eq{prop:reset:can}:
+  \begin{equation*}
     \AG \bigl(\PortFail(true) \rightarrow \EU[]{\lnot \PortFail(true)}{(\PortResume(true) \lor \PortReset)}\bigr).
-  \end{equation}
+  \end{equation*}
 is not true, because the $OT_2$ loop on state $\ostate{11}$ stays in

### 2019-02-14 2018-Arch-pNets/arch-pNets.tex
chasing footnotes again

@@
 the incoming arrows $\goesto{\TimerInit[]} \tstate{0}$ and
-$\goesto{\IntervalInit[]} \cstate{0}$.\footnote{%
-%
-  We use $\topinterval$ to denote the top interval in the inclusion
-  order, \ie $(-\infty, +\infty)$.
-%
-} The constants $\mathrm{Min}$ and $\mathrm{Max}$ are the parameters
+$\goesto{\IntervalInit[]} \cstate{0}$ where $\topinterval=(-\infty, +\infty)$.
+%\footnote{%
+%%
+%  We use $\topinterval$ to denote the top interval in the inclusion
+%  order, \ie $(-\infty, +\infty)$.
+%%
+%} 
+The constants $\mathrm{Min}$ and $\mathrm{Max}$ are the parameters
 of the architecture.
@@
 guards and update assignments of the transitions of $\NameCtrl$ are
-omitted. By default, an omitted guard is  $\true$ (true) and an omitted assignment is empty {\noop}.  
+omitted. By default, an omitted guard is  $\true$ and an omitted assignment is empty {\noop}.  
 %\noteLH{It looks like Max is in zone, I do not understand}

### 2019-02-15 2018-Arch-pNets/arch-pNets.tex
Contribs
bug \note

@@
 \newcommand{\todoLHin}[2][inline,color=orange!40]{\todo[#1]{\textbf{To-do Ludo: } {#2}}}
-\newcommand{\todoEM}[2][color=green!40, size=\tiny]{\todo[#1]{\textbf{To-do Eric:} {#2}}}
+\newcommand{\noteEM}[2][color=blue!40, size=\tiny]{\todo[#1]{{#2}\Eric}}
+\newcommand{\todoEM}[2][color=blue!40, size=\tiny]{\todo[#1]{\textbf{To-do Eric:} {#2}}}
 \newcommand{\noteEMin}[2][inline,color=green!40]{\todo[#1]{{#2}\Eric}}
@@
 
-The methodology we propose is thus to an encoding of BIP architectures into open pNet in order to be able to verify, using SMT techniques, the coordination capabilities of the architecture, and more generally its properties.
-The encoding will also give us feedback on the comparison between the BIP architectures and the pNet formalism.
-Overall, the encoding allows us to precisely compare the coordination mechanisms of the two models but also the way component composition is expressed in the two formalisms.
-This article is also the opportunity to investigate further on  compositional verification by relating two different composition mechanisms that provide different vision on compositional verification.
-\textbf{pas tres heureux la fin: pas assez detaille ou trop complique -> abstraire ou detailller a mon avis (Ludo)}
+The methodology we propose is thus to an encoding of BIP architectures
+into open pNet in order to be able to verify, using SMT techniques,
+the coordination capabilities of the architecture, and more generally
+its properties. The encoding will also give us feedback on the
+comparison between the BIP architectures and the pNet formalism.  
+Overall, the encoding allows us to precisely compare the coordination
+mechanisms of the two models but also the way component composition is
+expressed in the two formalisms. This article is also the opportunity
+to
+% investigate further on  compositional verification by
+relate two different composition mechanisms that provide different
+vision on compositional verification. \noteLH{pas tres heureux la fin:
+  pas assez detaille ou trop complique -> abstraire ou detailller a
+  mon avis (Ludo). J'ai prefere abstraire/raccourcir... (Eric)}
 
 \paragraph{Contributions}
+The main contributions of this paper are: 1) The definition of a
+theory of BIP architectures with data, including a theorem about
+preservation of (data dependent) properties by architecture
+compositions. 2) An encoding of architectures with data into the open pNet
+model, allowing for analysis of their temporal properties using pNet's
+software tools.
 

### 2019-02-15 2018-Arch-pNets/arch-pNets.tex
see def 10

--- 2019-02-14 2018-Arch-pNets/arch-pNets.tex
@@
 This article is also the opportunity to investigate further on  compositional verification by relating two different composition mechanisms that provide different vision on compositional verification.
-\textbf{pas tres heureux la fin: pas assez detaille ou trop complique -> abstraire ou detailller a mon avis (Ludo)}
+\noteLH{pas tres heureux la fin: pas assez detaille ou trop complique -> abstraire ou detailller a mon avis (Ludo)}\noteEM{j'ai prefere abstraire...}
 
@@
 $s^0_{\semopen{B}}$ the corresponding constituents of
-$\semopen{B}$.
+$\semopen{B}$ (see Definition~\ref{defn:comp:semantics}).
 

### 2019-02-15 2018-Arch-pNets/arch-pNets.tex
Compactage sec 2 et 3

--- 2019-02-15 2018-Arch-pNets/arch-pNets.tex
@@
 
-\paragraph{Contributions}
+%\paragraph{Contributions}
 The main contributions of this paper are: 1) The definition of a
@@
 
-\begin{proposition}[Properties of $\arcomp$]
-  \label{prop:arcomp:nice}
+%\begin{proposition}[Properties of $\arcomp$]
+%  \label{prop:arcomp:nice}
   %% Architecture composition
@@
   %% Furthermore, for any component $B$, we have $A_{id}(B) = \mu(B)$.
-\end{proposition}
+%\end{proposition}
 %
@@
 %% \end{proof}
-
 %% The last statement of \prop{arcomp:nice} highlights a subtle point:
@@
 %% not the identity operator on components.
-
 %****************************************************************
-\subsubsection{Preservation of safety properties}
-\label{secn:safety}
-
+%\subsubsection{Preservation of safety properties}
+%\label{secn:safety}
 For a component $B$, we denote $S_{\semopen{B}}$ and
 $s^0_{\semopen{B}}$ the corresponding constituents of
-$\semopen{B}$.
+$\semopen{B}$ (see Definition~\ref{defn:comp:semantics}).
 
@@
 \app{properties}.
-
 %% \todoSB{Cite the original paper somewhere.}
-The main idea of our approach is that an architecture enforces
-its characteristic property on the set of its operand components.
+An architecture enforces
+its characteristic property on  its operand components.
 From this point of view, the set of coordinating components is
-not relevant, neither are their states.  Thus, to talk about
-properties enforced by architectures, we consider properties on
-the unrestricted composition of the operand components as
-formalized by the following definition.
+not relevant, neither are their states.  Thus, 
+properties enforced by architectures only involve
+the unrestricted composition of the operands:
 
@@
 \end{definition}
-
-According to the above definition, when we say that an
-architecture enforces some property $\Phi$, it is implicitly
-assumed that $\Phi$ is initial for the coordinated components.
-Below, we omit mentioning this explicitly.
-
-\defn{up:compat} in \app{arch:appendix} provides a formal definition
-of the notion of \emph{upwards compatibility} needed to ensure property preservation when composing architectures relying on the maximal progress priority model.  Here, we present it
-informally due to page limitations.  Two architectures $A_1$ and $A_2$
-are said to be upwards compatible iff, whenever their composition
+In the following, when we say that an
+architecture enforces some property $\Phi$, $\Phi$ is supposed to be initial for the coordinated components.
+%
+%According to the above definition, when we say that an
+%architecture enforces some property $\Phi$, it is implicitly
+%assumed that $\Phi$ is initial for the coordinated components.
+%Below, we omit mentioning this explicitly.
+\defn{up:compat} in \app{arch:appendix} formally defines
+ \emph{upwards compatibility} that ensures property preservation when composing architectures. Informally, two architectures $A_1$ and $A_2$
+are  upwards compatible iff, whenever their composition
 involves the fusion of two interactions $a_1 = a \cap P_{A_1}$ and
-$a_2 = a \cap P_{A_2}$ (see \eq{arch:composition}), whereof one, say
+$a_2 = a \cap P_{A_2}$ (see \eq{arch:composition}) and one, say
 $a_1$, is inhibited in a given state by a larger interaction $b_1

### 2019-02-15 2018-Arch-pNets/arch-pNets.tex
compactage sec 2 et 3

@@
 }
+\setlength{\topsep}{0pt}%
 
@@
 software tools.
-
 The concepts and results of the paper are illustrated by a running
@@
 
-\section{General Notations and pNets previous results} 
+\section{General Notations and pNets Previous Results} 
 \label{secn:preliminaries}
@@
 $\pLTS\triangleq\mylangle S,s_0, \to\myrangle$ where:
-\begin{itemize}
-\item
-$S$ is a set of states, $\vars(s)$ denotes the set of associated variables;
-\item
-$s_0 \in S$ is the initial state;
+%\begin{itemize}
+%\item
+$S$ is a set of states; %$\vars(s)$ denotes the set of associated variables;
+%\item
+$s_0 \in S$ is the initial state; and
 %\item[$\bullet$]
@@
 %by the additional assignments.
-\item $\to \subseteq S \times L \times S$ is the transition relation and 
+%\item 
+$\to \subseteq S \times L \times S$ is the transition relation and 
 $L$ is the set of labels of the form
@@
 %\noteLH{COORDINATION: I believe we should remove the constraints}		
-\end{itemize}
+%\end{itemize}
 \end{definition}
@@
 K}\myrangle$
-where
+where\\[-3.5ex]
 \begin{itemize}
@@
   A component is a tuple $\tuple{Q, q^0, V, \val{0}{}, P,
-  \export, \goesto{}}$ where\\[-4ex]
+  \export, \goesto{}}$ where\vspace{-2ex}
   \begin{itemize}
@@
 The use of the intermediate valuation $\tilde{\val{}{}}$ in the
-conclusion and the third premise of rule \eq{comp:semantics}
-allows some of the variables to get new values before the
-transition is actually fired.  Thus the component is \emph{open}
+conclusion and the third premise of  \eq{comp:semantics}
+allows some  variables to get new values before the
+transition is  fired.  Thus the component is \emph{open}
 to the exchange of data with its environment.  However, the
-fourth premise in \eq{comp:semantics} restricts the set of
-variables that can be affected by such data transfer to those
-that are exported through the ports participating in the
-interaction.
+fourth premise  states that only the variables exported through the ports participating to the interaction can be affected by the data transfer.
+%restricts the set of
+%variables that can be affected by such data transfer to those
+%that are exported through the ports participating in the
+%interaction.
 
@@
   An \emph{architecture} is a tuple $A = \tuple{\cC, V_A, P_A,
-    \export[A], \Gamma}$, where
-%  
+    \export[A], \Gamma}$, where\vspace{-1.5ex}
   \begin{itemize}
@@
   the interaction model
-  over $(V, P, \export)$, with
-  \[
-  \export(p) = 
-  \begin{cases}
-    \export[C](p), & \text{for all } C \in \cC, p \in P_C,
-    \\
-    \export[B](p), & \text{for all } B \in \cB, p \in P_B,
-  \end{cases}
-  \]
+  over $(V, P, \export[C](p) \cup  \export[B](p))$ %, with  $\export(p) = \export[C](p) \cup  \export[B](p)$
+%\vspace{-1.5ex}
+%  \[
+%  \export(p) = 
+%  \begin{cases}
+%    \export[C](p), & \text{for all } C \in \cC, p \in P_C,
+%    \\
+%    \export[B](p), & \text{for all } B \in \cB, p \in P_B,
+%  \end{cases}
+%  \]
 %% defined by \noteLH{looks like this also depends on Pa}
@@
   $A_2$ is the architecture $A_1 \arcomp A_2 = \tuple{\cC_1 \cup \cC_2,
-  V_{A_1} \cup V_{A_2}, P_{A_1} \cup P_{A_2}, \export[A_1] \cup \export[A_2], \Gamma}$, where
+  V_{A_1} \cup V_{A_2}, P_{A_1} \cup P_{A_2}, \export[A_1] \cup \export[A_2], \Gamma}$, where\vspace{-1ex}
 %

### 2019-02-15 2018-Arch-pNets/arch-pNets.tex
arch-pNets paper (Minor): update to the defintion of the export function in Def 10 (Application of an architecture)
arch-pNets paper (Minor): update to the defintion of the export function in Def 10 (Application of an architecture) - reduced the size of parentheses
Quelques refs biblio

--- 2019-02-15 2018-Arch-pNets/arch-pNets.tex
@@
 
-The methodology we propose is thus to an encoding of BIP architectures into open pNet in order to be able to verify, using SMT techniques, the coordination capabilities of the architecture, and more generally its properties.
-The encoding will also give us feedback on the comparison between the BIP architectures and the pNet formalism.
-Overall, the encoding allows us to precisely compare the coordination mechanisms of the two models but also the way component composition is expressed in the two formalisms.
-This article is also the opportunity to investigate further on  compositional verification by relating two different composition mechanisms that provide different vision on compositional verification.
-\noteLH{pas tres heureux la fin: pas assez detaille ou trop complique -> abstraire ou detailller a mon avis (Ludo)}\noteEM{j'ai prefere abstraire...}
+The methodology we propose is thus to an encoding of BIP architectures
+into open pNet in order to be able to verify, using SMT techniques,
+the coordination capabilities of the architecture, and more generally
+its properties. The encoding will also give us feedback on the
+comparison between the BIP architectures and the pNet formalism.  
+Overall, the encoding allows us to precisely compare the coordination
+mechanisms of the two models but also the way component composition is
+expressed in the two formalisms. This article is also the opportunity
+to
+% investigate further on  compositional verification by
+relate two different composition mechanisms that provide different
+vision on compositional verification. \noteLH{pas tres heureux la fin:
+  pas assez detaille ou trop complique -> abstraire ou detailller a
+  mon avis (Ludo). J'ai prefere abstraire/raccourcir... (Eric)}
 
 \paragraph{Contributions}
+The main contributions of this paper are: 1) The definition of a
+theory of BIP architectures with data, including a theorem about
+preservation of (data dependent) properties by architecture
+compositions. 2) An encoding of architectures with data into the open pNet
+model, allowing for analysis of their temporal properties using pNet's
+software tools.
 
@@
 $s^0_{\semopen{B}}$ the corresponding constituents of
-$\semopen{B}$ (see Definition~\ref{defn:comp:semantics}).
+$\semopen{B}$.
 
@@
 infinite/parametrized model checking? == ERIC + Simon
+
+various classe infinite-state systems and/or paramaterized topologies
+via predicate abstraction and SMT satisfiability:
+\cite{DBLP:conf/cade/GhilardiNRZ08,DBLP:journals/corr/CimattiGMT13,DBLP:journals/corr/abs-1806-11459}
 

### 2019-02-15 2018-Arch-pNets/Arch-pNets_Before_shortening3.tex

--- 2019-02-15 2018-Arch-pNets/arch-pNets.tex
@@
 \newcommand{\todoLHin}[2][inline,color=orange!40]{\todo[#1]{\textbf{To-do Ludo: } {#2}}}
-\newcommand{\noteEM}[2][color=blue!40, size=\tiny]{\todo[#1]{{#2}\Eric}}
-\newcommand{\todoEM}[2][color=blue!40, size=\tiny]{\todo[#1]{\textbf{To-do Eric:} {#2}}}
+\newcommand{\todoEM}[2][color=green!40, size=\tiny]{\todo[#1]{\textbf{To-do Eric:} {#2}}}
 \newcommand{\noteEMin}[2][inline,color=green!40]{\todo[#1]{{#2}\Eric}}
@@
   \and
-	Univ Lyon, EnsL, UCBL, CNRS, Inria,  LIP, F-69342, LYON Cedex 07, France\\ \email{ludovic.henrio@ens-lyon.fr}
+	Univ Lyon, CNRS, ENS de Lyon, Inria, Universit\'e Claude Bernard Lyon 1, LIP, Lyon, France -- \email{ludovic.henrio@ens-lyon.fr}
   \and
@@
 
-The methodology we propose is thus to an encoding of BIP architectures
-into open pNet in order to be able to verify, using SMT techniques,
-the coordination capabilities of the architecture, and more generally
-its properties. The encoding will also give us feedback on the
-comparison between the BIP architectures and the pNet formalism.  
-Overall, the encoding allows us to precisely compare the coordination
-mechanisms of the two models but also the way component composition is
-expressed in the two formalisms. This article is also the opportunity
-to
-% investigate further on  compositional verification by
-relate two different composition mechanisms that provide different
-vision on compositional verification. \noteLH{pas tres heureux la fin:
-  pas assez detaille ou trop complique -> abstraire ou detailller a
-  mon avis (Ludo). J'ai prefere abstraire/raccourcir... (Eric)}
+The methodology we propose is thus to an encoding of BIP architectures into open pNet in order to be able to verify, using SMT techniques, the coordination capabilities of the architecture, and more generally its properties.
+The encoding will also give us feedback on the comparison between the BIP architectures and the pNet formalism.
+Overall, the encoding allows us to precisely compare the coordination mechanisms of the two models but also the way component composition is expressed in the two formalisms.
+This article is also the opportunity to investigate further on  compositional verification by relating two different composition mechanisms that provide different vision on compositional verification.
+\textbf{pas tres heureux la fin: pas assez detaille ou trop complique -> abstraire ou detailller a mon avis (Ludo)}
 
 \paragraph{Contributions}
-The main contributions of this paper are: 1) The definition of a
-theory of BIP architectures with data, including a theorem about
-preservation of (data dependent) properties by architecture
-compositions. 2) An encoding of architectures with data into the open pNet
-model, allowing for analysis of their temporal properties using pNet's
-software tools.
 
@@
 	\label{defn:open-automaton}
-	An \emph{open automaton} is a tuple $<\!\!J,\mathcal{S},s_0,\mathcal{T}\!\!>$ where:
-%	\begin{itemize}
-%		\item  
- $J$ is a  set of indices,
-%		\item 
-  $\mathcal{S}$ is a set of states and $s_0$ an initial state
+	An \emph{open automaton} is a structure\\ $A =
+	<J,\mathcal{S},s_0,\mathcal{T}>$ where:
+	\begin{itemize}
+		\item   $J$ is a  set of indices,
+		\item   $\mathcal{S}$ is a set of states and $s_0$ an initial state
 		among $\mathcal{S}$,
-%		\item 
-$\mathcal{T}$ is a set of open transitions and for each
+		\item $\mathcal{T}$ is a set of open transitions and for each
 		$t\in \mathcal{T}$ there exist  $J'$ with  $J'
@@
 		and  $\mathcal{S}$.
-%		
-%	\end{itemize}
+
+	\end{itemize}
 \end{definition}
@@
 tuples of states of the pLTSs at the leaves. We denote them $\triangleleft\ldots\triangleright$ for distinguishing tuple 
-states from other tuples. 
-%given by 
-%Definition~\ref{def-states}. 
-An open transition first
+states from other tuples. given by 
+Definition~\ref{def-states}. 
+The open transitions first
  project the global state into states of the leaves, then apply
-pLTS transitions on these states, and compose them with the actions of the holes according to the synchronisation vectors.
-More precisely, each open transition between two states is defined as a composition of transition from some pLTSs and actions of some holes as follows: 1) the actions of the holes involved in the transition, 2) a guard  built from the synchronisation vectors coordinating the holes and the transitions involved; 3) assignments and global state change are defined by the pLTSs transitions involved.
+pLTS transitions on these states, and compose them with the sort of the holes according to the synchronisation defined in the synchronisation vectors.
+More precisely, each open transition between two states is defined as a composition of transition from some pLTSs and actions of some holes as follows: 1) the actions of the holes involved in the transition, 2) a guard  built from the synchronisation vectors coordinating the holes and the transitions involved; 3) assignments defined by the pLTSs transitions involved.
 The synchronisation vectors also define the global action.
+The global state evolution is also defined by the set of state transitions of the pLTSs involved in the pLTSs.
 
@@
 
-This section presents the extension of the theory of
+\addSB{This section presents the extension of the theory of
   architectures \cite{AttieBBJS16-architectures-faoc} with data and
   briefly discusses a special case of priority models, called
-  \emph{maximal progress}.
+  \emph{maximal progress}.}
 
@@
 \label{secn:components}
-\begin{definition}[Component]
+
+\begin{definition}[Components]
   \label{defn:component}
-  A component is a tuple $\tuple{Q, q^0, V, \val{0}{}, P,
-  \export, \goesto{}}$ where\\[-4ex]
+  A \emph{component} is a tuple $\tuple{Q, q^0, V, \val{0}{}, P,
+  \export, \goesto{}}$, where
   \begin{itemize}
@@
     valuation} of the component variables, 
-  \item $P$ is a set of \emph{ports};
-    $\export : P \rightarrow 2^V$ is
+  \item $P$ is a set of \emph{ports}, with
+    $\export : P \rightarrow 2^V$ 
     the \emph{set of variables exported by each port},
@@
   We call the triple $(V,P, \export)$ the \emph{interface} of the
-  component.\,\footnote{Only exported variables, belonging to a
-  $\export(p)$, appear in the component interface  (see
-  \defn{im}).  We omit here this separation between internal and exported variables.
+  component.\,\footnote{%
+%
+  In practice, only exported variables, \ie those in the set
+  $\bigcup_{p \in P}\export(p)$, belong to the component interface and
+  can be used for the interactions with other components (see
+  \defn{im}).  In the context of this paper, we can simplify
+  by omitting this separation.
+%
   }
@@
 
-In this paper, we  use  a refined
+In this paper, we will use a running example, which is a refined
 version of the Failure Monitor architecture
-from~\cite{CubETH-case-study} as a running example.  Although \fig{schema:ArchFailure:BIP}
+from~\cite{CubETH-case-study}.  Although \fig{schema:ArchFailure:BIP}
 shows the full definition of this architecture, we will explain its
-various elements progressively.
-\fig{schema:ArchFailure:BIP} shows  components
+various elements progressively, as we define the corresponding
+notions.
+
+The model in \fig{schema:ArchFailure:BIP} has  components
 %% The
@@
   \{\PortTick, \PortCancel, \PortTOT\},
-  \bigl\{\!\PortTick \mapsto \{t, z\}\!\bigr\}
+  \bigl\{\PortTick \mapsto \{t, z\}\bigr\}
 }$,
@@
   \{\PortReset, \PortFail, \PortResume, \PortTOC\},
-  \bigl\{\!\PortFail \mapsto \{\mathit{zone}\}\!\bigr\}
-}$ respectively.
+  \bigl\{\PortFail \mapsto \{\mathit{zone}\}\bigr\}
+}$, respectively.
 %
@@
 Variable $t$ is implicitly assumed to be an integer.  Variables $z$
-and $\mathit{zone}$ are  integer intervals of
-the form $[l,u]$.  Both types are implicitly equipped with a
+and $\mathit{zone}$ are implicitly assumed to be integer intervals of
+the form $[l,u]$.  For both types, we also implicitly assume the
 natural ordering: increasing integers and interval inclusion.
@@
 the incoming arrows $\goesto{\TimerInit[]} \tstate{0}$ and
-$\goesto{\IntervalInit[]} \cstate{0}$ where $\topinterval=(-\infty, +\infty)$.
-%\footnote{%
-%%
-%  We use $\topinterval$ to denote the top interval in the inclusion
-%  order, \ie $(-\infty, +\infty)$.
-%%
-%} 
-The constants $\mathrm{Min}$ and $\mathrm{Max}$ are the parameters
+$\goesto{\IntervalInit[]} \cstate{0}$.\footnote{%
+%
+  We use $\topinterval$ to denote the top interval in the inclusion
+  order, \ie $(-\infty, +\infty)$.
+%
+} The constants $\mathrm{Min}$ and $\mathrm{Max}$ are the parameters
 of the architecture.
@@
 variables.  \Eg[,] the loop transition $\tstate{0}
-\goesto{\PortTick, \GuardTick[], \TimerUpd[]} \tstate{0}$. % in the
-%component $\NameTimer$ is labeled by the port $\PortTick$, the associated guarg and variable update. 
-% It can be
-%fired only when the current value of the local variable $t$ is less
-%than $z.u$.
-%%% , where $z = [l, u]$ is a local variable representing an
-%%% interval
-%Upon firing, this transition increments the value of $t$ by $1$.  
-The
+\goesto{\PortTick, \GuardTick[], \TimerUpd[]} \tstate{0}$ in the
+component $\NameTimer$ is labeled by the port $\PortTick$.  It can be
+fired only when the current value of the local variable $t$ is less
+than $z.u$.
+%% , where $z = [l, u]$ is a local variable representing an
+%% interval
+Upon firing, this transition increments the value of $t$ by $1$.  The
 guards and update assignments of the transitions of $\NameCtrl$ are
-omitted. By default, an omitted guard is  $\true$ and an omitted assignment is empty {\noop}.  
+omitted.  The default values are the constant predicate $\true$ (true) and
+the empty assignment {\noop}, respectively.  
 %\noteLH{It looks like Max is in zone, I do not understand}
@@
 fourth premise in \eq{comp:semantics} restricts the set of
-variables that can be affected by such data transfer to those
+variables, which can be affected by such data transfer, to those
 that are exported through the ports participating in the
@@
   for any interaction $(a, g, u) \in \Gamma$, we have
-  $g \in \guards{\export(a)}$ and $u \in \updates{\export(a)}$.\footnote{%
+  $g \in \guards{\export(a)}$ and $e \in \updates{\export(a)}$.\footnote{%
 %
@@
 %% \noteLH{supp should go outside the definition}
-We  
-assume that all sets of components and interfaces satisfy the disjointness assumption above.
+When speaking of a set of components or interfaces, we will always
+assume that it satisfies the disjointness assumption of \defn{im}.
 %
 We call the \emph{support} of a set of ports $a \subseteq P$, denoted
-$\supp{a}$, the set of the participating components. It is either the set $\setdef{i \in I}{a \cap P_i \neq
+$\supp{a}$, either the set $\setdef{i \in I}{a \cap P_i \neq
   \emptyset}$ (for $P = \bigcup_{i=1}^n P_i$) or the set $\setdef{B
@@
 P_B$).  The precise meaning of this notation will always be clear from
-the context.
+the context.  Intuitively, for an interaction $(a, g, u)$, $\supp{a}$
+denotes the set of the participating components.
 
@@
   q^0_i, V_i, \val{0}{i}, P_i, \export[i], \goesto{}}^{i \in I}$ with
-  the interaction model $\Gamma$ over $\tuple{V, P, \export}$
+  the interaction model $\Gamma$ over $\tuple{V, P, \export}$ (as in \defn{im})
   is the component $\Gamma(\cB) = \tuple{Q, q^0, V, \val{0}{}, P,
@@
 structure interactions in BIP models.
+
 Connectors are hierarchical, tree-like structures with component ports
@@
 The interaction model is defined as the set of all interactions
-allowed by at least one of the connectors.
+allowed by at least one of the connectors in the system.
 %% The composition semantics of BIP systems consists in
@@
 For instance, the connector {\NameTimer.\PortTick
-  \trigsynch (\PortFail \trigsynch \NameCtrl.\PortFail)} of \fig{schema:ArchFailure:BIP} is a
-two-level hierarchical connector.  In the  subconnector
+  \trigsynch (\PortFail \trigsynch \NameCtrl.\PortFail)} is a
+two-level hierarchical connector.  In the second-level subconnector
 {\PortFail \trigsynch \NameCtrl.\PortFail}, the port {\PortFail} is a
-trigger, whereas {\NameCtrl.\PortFail} is a synchron.  This
-subconnector allows two interactions: $\{\PortFail\}$ and $\listset{\NameCtrl.\PortFail, \PortFail}$.  Similarly, at the top level,
-{\NameTimer.\PortTick} is a trigger, and the 
-subconnector is a synchron. 
-% Hence, the overall connector allows the
-%interaction involving only one port {\NameTimer.\PortTick}\footnote{%
-%%
-%  Such interactions are called \emph{singleton interactions}.
-%%
-%} and any interaction involving both {\NameTimer.\PortTick} and
-%\emph{some} interaction of the second-level subconnector.  
-%Combining
-%the two levels we can see that t
-The entire connector defines the
+trigger, whereas {\NameCtrl.\PortFail} is a synchron.  Therefore, this
+subconnector allows two interactions labelled $\{\PortFail\}$ and $\listset{\NameCtrl.\PortFail, \PortFail}$.  Similarly, at the top level,
+{\NameTimer.\PortTick} is a trigger, whereas the second-level
+subconnector is a synchron.  Hence, the overall connector allows the
+interaction involving only one port {\NameTimer.\PortTick}\footnote{%
+%
+  Such interactions are called \emph{singleton interactions}.
+%
+} and any interaction involving both {\NameTimer.\PortTick} and
+\emph{some} interaction of the second-level subconnector.  Combining
+the two levels we can see that the entire connector defines the
 following three interactions (observe that $\topinterval +
@@
 %
-%\begin{gather*}
-$  \bigl(\{\NameTimer.\PortTick\},
+\begin{gather*}
+  \bigl(\{\NameTimer.\PortTick\},
   \true, \emptyset\bigr)
   %% \NameTimer.z := \NameTimer.z\bigr)
- $,
-$  \bigl(\{\PortFail, \NameTimer.\PortTick\},
-  \true, \emptyset\bigr)$
+  ,
+%
+  \qquad
+%
+  \bigl(\{\PortFail, \NameTimer.\PortTick\},
+  \true, \emptyset\bigr)
   %% \NameTimer.z := \NameTimer.z\bigr)
   ,
-$
+%
+  \\
+%
   \bigl(\{\NameCtrl.\PortFail, \PortFail, \NameTimer.\PortTick \},
@@
   \NameTimer.z := \NameTimer.z \cap (\NameCtrl.\mathit{zone} + \NameTimer.t)\bigr)
-$
-%  .
-%\end{gather*}
+  .
+\end{gather*}
 %% \begin{align*}
@@
 
-\addSB{In addition to interaction models, BIP relies on 
-  \emph{priority models} that impose  a strict partial order on
+\addSB{In addition to interaction models, BIP relies on the so-called
+  \emph{priority models}, imposing a strict partial order on
   interactions.  Formal definitions are provided in \app{arch:appendix}.  Intuitively, an interaction can be fired only if all
@@
 %
-In the next sections, we will implicitly assume application of the  \emph{maximal
+In the results and the running example of this paper, we will implicitly assume application of the so-called \emph{maximal
   progress} priority $\mu$, where $(a, g, u) \prec_\mu (b, h, w)$ iff  $a \subset b$ and $a \neq b$.  For instance, the
-port $\NameTimer.\PortTick$ will never fire alone if the port $\PortFail$ is also enabled.
-In \secn{conclusion}, we discuss the generalisation of the
+port $\NameTimer.\PortTick$ will never fire alone in a global state,
+where the \noteSB{This turns out to be the first use of the word. I am tempted to pretend I did not notice.}\hl{dangling} port $\PortFail$ is also enabled.
+In \secn{conclusion}, we discuss the possibility of generalising the
 obtained results to other priority models.
@@
 
-Architectures are partial BIP models, with \emph{dangling}
-ports that serve as placeholders for the eventual connection with
- \emph{operand} components.
+Architectures are partially defined BIP models, where \emph{dangling}
+ports serve as placeholders for the eventual connection with
+additional \emph{operand} components.
 
@@
 %
-  and $\mu(...)$ denotes the application of the maximal progress priority model.
+  and $\mu$ is the maximal progress priority model.
 \end{definition}
@@
 infinite/parametrized model checking? == ERIC + Simon
-
-various classe infinite-state systems and/or paramaterized topologies
-via predicate abstraction and SMT satisfiability:
-\cite{DBLP:conf/cade/GhilardiNRZ08,DBLP:journals/corr/CimattiGMT13,DBLP:journals/corr/abs-1806-11459}
 

### 2019-02-15 2018-Arch-pNets/arch-pNets.tex
Compacted the begining

--- 2019-02-15 2018-Arch-pNets/arch-pNets.tex
@@
 \institute{%
-  Inria Lille -- Nord Europe, Villeneuve d'Ascq, France\\
+  Inria Lille -- Nord Europe, Villeneuve d'Ascq, France \\
   \email{simon.bliudze@inria.fr}
@@
 architectures preserves their characteristic safety properties.
-
 To verify that individual architectures do enforce their associated
-properties, we provide a non-trivial encoding into an intermediate
-model called open pNets that supports SMT-based verification.
-Additionally, the translation into the open pNet semantic model gives
+properties, we provide an encoding into open pNets, an intermediate
+model  that supports SMT-based verification.
+Additionally, the translation into  open pNet  gives
 us a strong insight and a comparison of the coordination mechanisms
@@
 
-\keywords{Parametrised verification, composition, safety, interaction
+\keywords{Verification, composition, safety, interaction
   models.}
@@
 implement the BIP operational semantics~\cite{BliSif08-acp-tc}.
-This approach ensures that any property, shown to hold on a given BIP
-model, will also hold by construction on the generated code.
-
-In this context, the notion of \emph{architecture} was proposed
+BIP ensures that any property that holds on a BIP
+model will also hold on the generated code.
+The notion of BIP \emph{architecture} was proposed
 in~\cite{AttieBBJS16-architectures-faoc} as a mechanism for ensuring
@@
 %% }
-and applied to the model, thereby potentially introducing additional
-coordinator components and modifying the connectors that define
-synchronisation patterns among ports of components.
+and applied to the model, adding
+coordinator components and modifying the 
+synchronisation patterns between components.
 In~\cite{AttieBBJS16-architectures-faoc}, it was shown that
 application of architectures is compositional \wrt safety properties,
-\ie when several architectures are applied, each enforcing a safety
-property, the resulting system satisfies their conjunction.
-
-This article goes one step further in the proof of properties and in the compositionality of architectures, but this step is a significant one as it targets verification and consequently compositional verification.
-To ensure properties of BIP architectures
+\ie if two architectures guarantee two properties, their composition ensure the conjunction of the properties.
+%
+%several architectures are applied, each enforcing a safety
+%property, the resulting system satisfies their conjunction.
+
+This article goes one step further in the proof of properties and in the compositionality of architectures, but this step is a significant one: the compositional verification.
+To prove properties of BIP architectures
 it is necessary to have a representation of the BIP architecture in a verifiable format. 
 The verification problem has two unbounded parameters: 1) By nature, architectures have holes and are meant to interact with the interfaces of the component that will fill the hole; the properties must hold for all (well-typed) components that can be put inside the hole; 2) BIP interactions can transmit data, and properties might be dependent of the data, the domain of the data is generally huge or unbound and the value of transmitted data might have a significant impact on the properties.
-
-Due to the nature of the problem, we propose to rely on a translation of BIP architectures into pNets, a direct verification of BIP could also be possible but pNets already have a verification tools based on a SMT solver, and doing the same work for BIP would require  a large amount of similar development.
-More interestingly, relying on a translation to pNets allow us to compare the two models, as discussed below.
-
-Parameterised Networks of synchronised automata (pNets) is a formalism for defining behavioural specification of distributed systems.
+Due to the nature of the problem, we propose to rely on a translation of BIP architectures into pNets, a direct verification of BIP could  be possible but pNets already have verification tools based on a SMT solver, and doing the same work for BIP would require  a large amount of similar development.
+More interestingly, relying on a translation to pNets allow us to compare the two models.
+
+Parameterised Networks of synchronised automata (pNets) is a formalism for defining behavioural specification of distributed systems based on a parametrised and hierarchical model.
 It inherited from the work of
 Arnold on synchronisation vectors~\cite{Arnold1982}. 
-In previous work~\cite{HMZ:PDP15}, it was shown pNets can be used to represent the behavioural semantics
+It has been shown work~\cite{HMZ:PDP15} that pNets can  represent the behavioural semantics
 of a system 
-including value-passing and many kinds of synchronisation methods. We
-used these results to give the semantics of various constructs and
-languages for distributed objects, and to build a platform for design
-and verification of distributed software components
+including value-passing and many kinds of synchronisation methods, including various constructs and
+languages for distributed objects. The Vercors  platform uses pNets to design
+and verify  distributed software components
 \cite{CM:FMCO08,HKM-FASE16}. 
-By nature, pNets is a  parametrised and hierarchical model.
-Their structure is static, but unbounded, and this allows for model-checking
+pNets structure is static, but unbounded,  this allows for model-checking
 approaches even for reconfigurable applications.
@@
 while open pNets have ``holes'', playing the role of process
-parameters. Such open systems can be used to define composition operators or structuring architectures.
+parameters. Such open systems can represent composition operators or structuring architectures.
 It is possible to reason, in an SMT engine, on the symbolic automaton that represents the behaviour of a pNets with holes and that communicates value~\cite{HMZ-FORTE2016QBMZ-AVOCS18}.
 This encoding of open pNets into Z3 that is under development is the starting point of this article.
-Our objective is to benefit from the possibility to reason on a pNet in an SMT engine in order to prove properties on BIP architectures.
-
-The methodology we propose is thus to an encoding of BIP architectures
-into open pNet in order to be able to verify, using SMT techniques,
-the coordination capabilities of the architecture, and more generally
-its properties. The encoding will also give us feedback on the
+We benefit from the possibility to reason on a pNet in an SMT engine in order to prove properties on BIP architectures.
+
+Wwe propose   to encode BIP architectures
+into open pNet and to verify, using SMT techniques,
+the coordination capabilities of the architecture, and 
+its properties. The encoding will  give us feedback on the
 comparison between the BIP architectures and the pNet formalism.  
@@
 mechanisms of the two models but also the way component composition is
-expressed in the two formalisms. This article is also the opportunity
+expressed in the two formalisms. This  also gives the opportunity
 to
 % investigate further on  compositional verification by
-relate two different composition mechanisms that provide different
-vision on compositional verification. \noteLH{pas tres heureux la fin:
-  pas assez detaille ou trop complique -> abstraire ou detailller a
-  mon avis (Ludo). J'ai prefere abstraire/raccourcir... (Eric)}
+relate two  different
+visions on compositional verification. 
+%\noteLH{pas tres heureux la fin:
+%  pas assez detaille ou trop complique -> abstraire ou detailller a
+%  mon avis (Ludo). J'ai prefere abstraire/raccourcir... (Eric)}
 
@@
 For a valuation $\val{}{}$ and an assignment $(x_i := e_i)^{i \in I}$, we define:
+\vspace{-1.2ex}
 \[
@@
 
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=0.9\columnwidth]{BIPspec-ArchFailureTimerMax-v4}
+  \caption{The BIP specification of the Failure Monitor architecture}
+  \label{fig:schema:ArchFailure:BIP}
+\end{figure}
+
 %\paragraph{Operational Semantics.}
@@
 	Where $s, s'\in\mathcal{S}$ and $\beta_j\in\actions{\variables}$
-        is an action of the hole $j$. $v$ is a variable denoting the resulting action
-        of this open transition. \Pred\ is a predicate 
+        is an action of the hole $j$. $\alpha$ is the resulting global action. \Pred\ is a predicate 
 	over the different variables of the
@@
 
-We build the semantics of open pNets as an open automaton where  the states are
-tuples of states of the pLTSs at the leaves. We denote them $\triangleleft\ldots\triangleright$ for distinguishing tuple 
-states from other tuples. 
-%given by 
-%Definition~\ref{def-states}. 
-An open transition first
- project the global state into states of the leaves, then apply
-pLTS transitions on these states, and compose them with the actions of the holes according to the synchronisation vectors.
-More precisely, each open transition between two states is defined as a composition of transition from some pLTSs and actions of some holes as follows: 1) the actions of the holes involved in the transition, 2) a guard  built from the synchronisation vectors coordinating the holes and the transitions involved; 3) assignments and global state change are defined by the pLTSs transitions involved.
-The synchronisation vectors also define the global action.
+The semantics of an open pNets is an open automaton where  the states are
+tuples of states of the pLTSs at the leaves, denoted $\triangleleft\ldots\triangleright$.
+Each open transition between two states is defined as a composition of transition from some pLTSs and actions of some holes as follows: 1) the actions of the holes involved in the transition, 2) a guard  built from the synchronisation vectors coordinating the holes and the transitions involved; 3) assignments and global state change are defined by the pLTSs transitions involved.
+The synchronisation vectors also define a global action.
 
@@
 
-pNets have already been used to define a behavioural semantics for distributed components~\cite{AmeurBoulifa2017}, in these works, from a pNet model with finite instantiations of parameters, correctness properties can be verified by model-checking.
-More recently, a bisimulation theory with composition properties have been formalised for open pNets~\cite{HMZ-FORTE2016}, and a SMT framework has been developed  for verifying properties of parametrised open pNets.
+With pNets, we can define a behavioural semantics for distributed components~\cite{AmeurBoulifa2017} where correctness properties are verified by model-checking. 
+More recently, a bisimulation theory has been formalised for open pNets~\cite{HMZ-FORTE2016}.
 
@@
 
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=0.9\columnwidth]{BIPspec-ArchFailureTimerMax-v4}
-  \caption{The BIP specification of the Failure Monitor architecture}
-  \label{fig:schema:ArchFailure:BIP}
-\end{figure}
-
 In this paper, we  use  a refined
@@
   the interaction model
-  over $(V, P, \export[C](p) \cup  \export[B](p))$ %, with  $\export(p) = \export[C](p) \cup  \export[B](p)$
+  over $\tuple{V, P, \export[A] \cup  \bigcup_{B \in \cB}\export[B]}$ %, with  $\export(p) = \export[C](p) \cup  \export[B](p)$
 %\vspace{-1.5ex}
@@
 %
-  and $\mu(...)$ denotes the application of the maximal progress priority model.
+  and $\mu(\dots)$ denotes the application of maximal progress.
 \end{definition}
@@
 
-A few tracks
+A few tracks, pas r\'edig\'es...
 
@@
 infinite/parametrized model checking? == ERIC + Simon
+Basic models for data-sensitive infinite systems: Hennesy \& Lin's value-passing systems with assignments \cite{CONCUR::Lin1996,HennessyL1995:353,APSEC::Lin2001}
+
+various classe infinite-state systems and/or paramaterized topologies
+via predicate abstraction and SMT satisfiability:
+\cite{BruniEtAl-Tiles-Concur2000,DBLP:conf/cade/GhilardiNRZ08,DBLP:journals/corr/CimattiGMT13,DBLP:journals/corr/abs-1806-11459}
 

### 2019-02-15 2018-Arch-pNets/arch-pNets.tex
more bib

--- 2019-02-15 2018-Arch-pNets/arch-pNets.tex
@@
 
-A few tracks
+%%A few tracks, pas r\'edig\'es...
 
@@
 
-infinite/parametrized model checking? == ERIC + Simon
+%% infinite/parametrized model checking? == ERIC (listes ci-dessous)  + Simon
+
+Basic research on behaviour models and verification algorithms for
+data-sensitive systems started in the nineties, with the seminal work
+of Hennesy, Lin, and their colleagues on value-passing systems with
+assignments
+\cite{CONCUR::Lin1996,HennessyL1995:353,APSEC::Lin2001}. Later, many
+different works addressing various classes of infinite-state systems
+and/or paramaterized topologies have been published, using
+combinations of approaches, often including predicate abstraction and
+SMT satisfiability (see
+e.g. \cite{BruniEtAl-Tiles-Concur2000,DBLP:conf/cade/GhilardiNRZ08,DBLP:journals/jsat/AlbertiGPRR12,CimattiEtAl-NUXMV-CAV2014,ChampionEtAl-Kind2-CAV2016}). With
+respect to these, we use symbolic representations not only to get a
+finite representation of infinite spaces, but also to express the
+(data-sensitive) synchronisations with the environment, making our
+models suitable for compositional verification.
+
+Among these works, several have shown the capacity of the SMT engines
+(either Z3 or Yikes) as servers for solving verification conditions of
+the algorithms, for large case-studies
+(e.g. \cite{DBLP:journals/corr/CimattiGMT13,DBLP:journals/corr/abs-1806-11459}).
+%% SMT on an application not using component structure. is there a strong Z3 example == Eric
 
@@
 In this paper, we rely on automatic encoding into a SMT solver making the proof of properties much more automatic, but we cannot prove the safety of the reconfiguration procedure.
-
-SMT on an application not using component structure. is there a strong Z3 example == Eric
 

### 2019-02-15 2018-Arch-pNets/arch-pNets.tex

--- 2019-02-15 2018-Arch-pNets/arch-pNets.tex
@@
 
-A few tracks, pas r\'edig\'es...
+%%A few tracks, pas r\'edig\'es...
 
@@
 
-infinite/parametrized model checking? == ERIC + Simon
-Basic models for data-sensitive infinite systems: Hennesy \& Lin's value-passing systems with assignments \cite{CONCUR::Lin1996,HennessyL1995:353,APSEC::Lin2001}
-
-various classe infinite-state systems and/or paramaterized topologies
-via predicate abstraction and SMT satisfiability:
-\cite{BruniEtAl-Tiles-Concur2000,DBLP:conf/cade/GhilardiNRZ08,DBLP:journals/corr/CimattiGMT13,DBLP:journals/corr/abs-1806-11459}
+%% infinite/parametrized model checking? == ERIC (listes ci-dessous)  + Simon
+
+Basic research on behaviour models and verification algorithms for
+data-sensitive systems started in the nineties, with the seminal work
+of Hennesy, Lin, and their colleagues on value-passing systems with
+assignments
+\cite{CONCUR::Lin1996,HennessyL1995:353,APSEC::Lin2001}. Later, many
+different works addressing various classes of infinite-state systems
+and/or paramaterized topologies have been published, using
+combinations of approaches, often including predicate abstraction and
+SMT satisfiability (see
+e.g. \cite{BruniEtAl-Tiles-Concur2000,DBLP:conf/cade/GhilardiNRZ08,DBLP:journals/jsat/AlbertiGPRR12,CimattiEtAl-NUXMV-CAV2014,ChampionEtAl-Kind2-CAV2016}). With
+respect to these, we use symbolic representations not only to get a
+finite representation of infinite spaces, but also to express the
+(data-sensitive) synchronisations with the environment, making our
+models suitable for compositional verification.
+
+Among these works, several have shown the capacity of the SMT engines
+(either Z3 or Yikes) as servers for solving verification conditions of
+the algorithms, for large case-studies
+(e.g. \cite{DBLP:journals/corr/CimattiGMT13,DBLP:journals/corr/abs-1806-11459}).
+%% SMT on an application not using component structure. is there a strong Z3 example == Eric
 

### 2019-02-15 2018-Arch-pNets/arch-pNets.tex
3 sec in 9 pages

--- 2019-02-15 2018-Arch-pNets/arch-pNets.tex
@@
 
-Wwe propose   to encode BIP architectures
+We propose   to encode BIP architectures
 into open pNet and to verify, using SMT techniques,
-the coordination capabilities of the architecture, and 
-its properties. The encoding will  give us feedback on the
-comparison between the BIP architectures and the pNet formalism.  
+the properties of the architectures. The encoding also allows us to
+compare BIP architectures and  pNet formalism.  
 Overall, the encoding allows us to precisely compare the coordination
@@
 theory of BIP architectures with data, including a theorem about
-preservation of (data dependent) properties by architecture
-compositions. 2) An encoding of architectures with data into the open pNet
-model, allowing for analysis of their temporal properties using pNet's
+preservation of (data dependent) properties by 
+compositions. 2) An encoding of architectures with data into  open pNets, allowing for analysis of their temporal properties using pNet's
 software tools.
-The concepts and results of the paper are illustrated by a running
-example extending the Failure Monitor architecture from the CubETH
-nanosatellite on-board software case study~\cite{CubETH-case-study}.
+The  paper is illustrated by a running
+example based on the failure monitor architecture from the CubETH
+nanosatellite on-board software~\cite{CubETH-case-study}.
 
@@
 
-\subsection{Notations}
+\subsubsection{Notations.}
 \label{secn:notations}
@@
 $\valuations{V} \bydef{=} \{\val{}{}: V \rightarrow \data\}$
-the set of \emph{valuations} of the variables in $V$.
-Valuations extend canonically to expressions and denote $\val{}{}(e)$ the value of $e$ under the valuation $\val{}{}$.
+the set of \emph{valuations} of the variables in $V$ and let $\sigma$ range over valuations.
+Valuations extend canonically to expressions, denoted $\val{}{}(e)$. We define:
 %\noteLH{its the following really necessary}
@@
 %  $\exprs{V} \rightharpoonup \data$.}
-For a valuation $\val{}{}$ and an assignment $(x_i := e_i)^{i \in I}$, we define:
-\vspace{-1.2ex}
+%For a valuation $\val{}{}$ and an assignment $(x_i := e_i)^{i \in I}$, we define:
+\vspace{-1.5ex}
 \[
@@
   \val{}{}(e_i), & \text{if } x = x_i, \text{for some } i \in I\,.
-\end{cases}
+\end{cases}\vspace{-1ex}
 \]
@@
 
-\subsection{Open pNets}
+\subsubsection{Open pNets.}
 \label{secn:pNets}
@@
 set of \emph{synchronisation vectors} that express the possible
-synchronisation between the parameterised actions of a subset of the
-sub-trees.
+synchronisation between  parameterised actions of some components.
 
@@
 $\alpha=a(?x_i^{i \in I}, 
-\Expr_j^{j \in J})$, where $?x_i^{i \in I}$ are input variables, $\Expr_j^{j \in J}$ 
+e_j^{j \in J})$, where $?x_i^{i \in I}$ are input variables, $e_j^{j \in J}$ 
 are expressions.
@@
 %sort~\cite{HMZ-FORTE2016}}:
-$\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, J, \symb{SV}_k^{k\in 
+$Q\triangleq \pLTS~|~\mylangle Q_i^{i\in I}, J, \symb{SV}_k^{k\in 
 K}\myrangle$
@@
 \begin{itemize}
-\item $\pNet_i^{i\in I}$ is the family of sub-pNets;
-%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which 
+\item $Q_i^{i\in I}$ is the family of sub-pNets;
+%  $Q_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which 
 %sub-pNets are indexed.
@@
 %\item
-The set of \emph{holes} $\Holes(\pNet)$ of a pNet is the indexes of the holes of the pNet 
+The set of \emph{holes} $\Holes(Q)$ of a pNet is the indexes of the holes of the pNet 
 itself plus the indexes of all the holes of its subnets (we suppose those indexes 
@@
 The set of \emph{leaves} of a pNet is the set of all pLTSs occurring in the structure, as an 
-indexed family of the form $\Leaves(\pNet)= \mylangle \pNet_i \myrangle^{i \in L}$.
+indexed family of the form $\Leaves(Q)= \mylangle \pLTS_i \myrangle^{i \in L}$.
 %\end{itemize}
@@
 \end{definition}
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=0.9\columnwidth]{BIPspec-ArchFailureTimerMax-v4}
-  \caption{The BIP specification of the Failure Monitor architecture}
-  \label{fig:schema:ArchFailure:BIP}
-\end{figure}
 
@@
 tuples of states of the pLTSs at the leaves, denoted $\triangleleft\ldots\triangleright$.
-Each open transition between two states is defined as a composition of transition from some pLTSs and actions of some holes as follows: 1) the actions of the holes involved in the transition, 2) a guard  built from the synchronisation vectors coordinating the holes and the transitions involved; 3) assignments and global state change are defined by the pLTSs transitions involved.
-The synchronisation vectors also define a global action.
+Each open transition between two states contains 1) the actions of the holes involved in the transition, 2) a guard  built from the synchronisation vectors coordinating the holes and the transitions involved; 3) assignments and global state change  defined by the pLTSs transitions involved; 4) a global action  defined by the synchronisation vector.
 
@@
 
-With pNets, we can define a behavioural semantics for distributed components~\cite{AmeurBoulifa2017} where correctness properties are verified by model-checking. 
-More recently, a bisimulation theory has been formalised for open pNets~\cite{HMZ-FORTE2016}.
-
 %\todoLHin{add a paragraph about pnets properties and usage, here are a few points (to be completed and written up properly depending on what we need}
@@
 
+We  used pNets to define a behavioural semantics for distributed components~\cite{AmeurBoulifa2017} that allows the verification of correctness properties  by model-checking. 
+More recently, a bisimulation theory has been formalised for open pNets~\cite{HMZ-FORTE2016}.
+
 %****************************************************************
@@
 of the architecture.
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=0.9\columnwidth]{BIPspec-ArchFailureTimerMax-v4}
+  \caption{The BIP specification of the Failure Monitor architecture}
+  \label{fig:schema:ArchFailure:BIP}
+\end{figure}
 

### 2019-02-15 2018-Arch-pNets/arch-pNets.tex
added dessin du dernier OA

@@
 
-\subsection{Verification of the characteristic properties}
+%% \subsection{Verification of the characteristic properties}
+%% Eric: je pense que ce soutitre est inutile...
+
 \label{secn:arch:verif}
@@
 readability. This comes as a complement to the open automaton in
-Fig. \ref{schema:ArchFailure:OA}, in which we only have a partial view
+Fig. \ref{schema:ArchFailure:OA-annex}, in which we only have a partial view
 of the OTs details.
@@
   \caption{The open Automaton of the Failure Monitor Architecture}
-  \label{schema:ArchFailure:OA}
+  \label{schema:ArchFailure:OA-annex}
 \end{figure}
@@
 
-  In Fig. \ref{schema:ArchFailure:OA}, you can see that some
+  In Fig. \ref{schema:ArchFailure:OA-annex}, you can see that some
   properties from appendix \app{properties} do not hold.
@@
 
-\small\begin{verbatim}
+\begin{verbatim}
   {t1---tick(z, t, z1)-->t1, s1---fail(zone, true, false)-->s1},
   {B|->fail(b0:sva_SV0)},
-            [(t<(GET_MAX z))/\((tick(z, t, z1))=(tick(z:sva_SV0, t:sva_SV0, z1:sva_SV0)))
+    [(t<(GET_MAX z))
+     /\((tick(z, t, z1))=(tick(z:sva_SV0, t:sva_SV0, z1:sva_SV0)))
      /\((fail(zone, true, false))=(fail(zone:sva_SV0, bf:sva_SV0, b1:sva_SV0)))
@@
      /\((bf:sva_SV0/\b0:sva_SV0)=>b1:sva_SV0)
-              /\(z1:sva_SV0=(z:sva_SV0 |Intersection| ((b1:sva_SV0?(zone:sva_SV0):(TopInt))+t:sva_SV0)))],
+     /\(z1:sva_SV0=(z:sva_SV0 |Intersection|
+                    ((b1:sva_SV0?(zone:sva_SV0):(TopInt))+t:sva_SV0)))],
  {t := t+1, z := z1}
@@
 
-\todoEM{Il faudrait (mais a-t-on le temps?): faire un dessin de la
+\medskip
+\noteEMin{Il faudrait (mais a-t-on le temps?): faire un dessin de la
   composition au niveau BIP, et au niveau pNet. Un resultat brut, vaguement
-  correct, montre 36 OTs, modulo les petites questions de mon mail de
+  correct, montre 37 OTs, modulo les petites questions de mon mail de
   mercredi midi...
-  Au moins dessiner cet automate, et ecrire les proprietes qu'il
-  verifie... }
-
-Primary version of the composed pNet:
-
+
+  J'ai une version simplifiee de cet automate ci-dessous.
+
+  Ecrire les proprietes qu'il verifie... ? }
+
+Here is the code of the corresponding composed pNet:
+
+\medskip
 \begin{verbatim}
-SV0: <tick(z, t, z1), fail(zone1, b11), fail(zone2, b12), fail1(b01), fail2(b02), _> --> fail(b01, b02), 
-     (z1 = z |Intersection| ((b11?zone1:TopInt)+t) |Intersection| ((b12?zone2:TopInt)+t))
-     /\(b11=>b01)/\(b12=>b02)
-SV1: <cancel(b1), resume(b21), resume(b22), resume1, resume2, _>-->resume, (b1=b21)/\(b1=b22)
+SV0: <tick(z, t, z1), fail(zone1, b11), fail(zone2, b12), fail1(b01), fail2(b02), _> 
+     --> fail(b01, b02), 
+     [(z1 = z |Intersection| ((b11?zone1:TopInt)+t) |Intersection| ((b12?zone2:TopInt)+t))
+      /\(b11=>b01)/\(b12=>b02)]
+SV1: <cancel(b1), resume(b21), resume(b22), resume1, resume2, _>-->resume, 
+     [(b1=b21)/\(b1=b22)]
 SV2: <timeout, timeout, timeout, _, _, ask>-->ask
@@
 
+  \begin{figure}[h]
+  \centering
+  \includegraphics[width=\columnwidth]{TimerV4X2}
+  \caption{The open Automaton of the composed system}
+  \label{schema:ArchFailure:OA-TimerV4X2}
+\end{figure}
+
 \end{document}

### 2019-02-16 2018-Arch-pNets/arch-pNets.tex
small saterday morning commit

@@
 %on the finite branching of the transition relation.
+Variables of each state are parwise disjoint.
 We need to introduce input variables to reason about the data flow between actions.
-We  define the set of actions a pLTS can use ($a$
+We  define the set of parameterised actions a pLTS can use ($a$
 ranges over action labels):\\
@@
 
-The semantics of an open pNets is an open automaton where  the states are
+The semantics of an open pNet is an open automaton where  the states are
 tuples of states of the pLTSs at the leaves, denoted $\triangleleft\ldots\triangleright$.
@@
   \bigl\{\!\PortFail \mapsto \{\mathit{zone}\}\!\bigr\}
-}$ respectively.
+}$
+\noteEM{Attention, bug dans la figure 2, ou tu mets $reset\mapsto \mathit{zone}$}{respectively}.
 %
@@
 \tstate{0} and \cstate{0}, and valuations $\val{0}{\NameTimer} = \{t
-\mapsto 0, z \mapsto \topinterval\}$ and $\val{0}{\NameCtrl} =
+\mapsto 0, z \mapsto \topinterval\}$
+$\val{0}{\NameCtrl} =
 \{\mathit{zone} \mapsto [\mathrm{Min}, \mathrm{Max}]\}$ are shown by
@@
 
-\paragraph{Encoding the coordinators}
+\paragraph{Encoding the coordinators.}
 To encode a coordinator $C$, we 1)~introduce a fresh initial state with an additional
@@
 \label{secn:conclusion}
+
+Discussion:
+
+- what did we lern about comparison of the coordination models ?
+
+- extension to other priority features
+
+- proof of correctness ?
 

### 2019-02-16 2018-Arch-pNets/arch-pNets.tex
sections 2 and 4

@@
 compositional application of verified design patterns\mdash which we
-call \emph{architectures}\mdash to a minimal set of functional
+call \emph{architectures}\mdash to a \noteEM{ca veut dire quoi, minimal? On enleve ?}minimal set of functional
 components.  To this end, we extend the theory of architectures
@@
 
-\keywords{Verification, composition, safety, interaction
+\keywords{Verification, \noteEM{Je mettrais bien symbolic quelque part...}symbolic automaton, composition, safety, interaction
   models.}
@@
 Due to the nature of the problem, we propose to rely on a translation of BIP architectures into pNets, a direct verification of BIP could  be possible but pNets already have verification tools based on a SMT solver, and doing the same work for BIP would require  a large amount of similar development.
-More interestingly, relying on a translation to pNets allow us to compare the two models.
+More interestingly, relying on a translation to pNets allows us to compare the two models.
 
@@
 including value-passing and many kinds of synchronisation methods, including various constructs and
-languages for distributed objects. The Vercors  platform uses pNets to design
+languages for distributed objects. The VerCors  platform uses pNets to design
 and verify  distributed software components
@@
 We propose   to encode BIP architectures
-into open pNet and to verify, using SMT techniques,
+into open pNets and to verify, using SMT techniques,
 the properties of the architectures. The encoding also allows us to
@@
 mechanisms of the two models but also the way component composition is
-expressed in the two formalisms. This  also gives the opportunity
-to
-% investigate further on  compositional verification by
-relate two  different
-visions on compositional verification. 
+expressed in the two formalisms. \noteEM{J'ai vire une phrase un peu
+  redondante avec la phrase precedente, et deja une autre 20 lignes
+  plus haut... }
+%This also gives the opportunity
+%to relate two  different visions on compositional verification.
+
 %\noteLH{pas tres heureux la fin:
@@
 %\item
-$s_0 \in S$ is the initial state; and
+$s_0 \in S$ is the initial state;
 %\item[$\bullet$]
@@
 %pNets as constructors for hierarchical behavioural structures.
-A pNet composes several pNets, pLTSs, and holes playing the role of process parameters.
+A pNet composes several pNets, pLTSs, and holes.
 A  pNet  exposes
@@
 \renewcommand{\Post}{u}
-The semantics of an open pNets is expressed as  an automaton where each transition composes the actions of several holes, 
+The semantics of an open pNet is expressed as  an automaton where each transition \noteEM{remplacer composes par ``coordinates'' ?}composes the actions of several holes, 
 the transition occurs if some predicates hold, and can involve  
@@
 \end{small}
-%
-%The first one, $OT_1$, corresponds to the simultaneous initialisation
-%of both controlers. No hole is active at that time, and the resulting
-%global action is denoted $\alpha_4$.
 It requires the hole at label $B$ to fire a $fail(b)$ action, with the condition $b=true$ and the state variable $t<Max$.
@@
 \paragraph{Encoding the coordinators.}
-To encode a coordinator $C$, we 1)~introduce a fresh initial state with an additional
+The encoding of a coordinator $C$ is a pLTS where we: 1)~introduce a
+fresh initial state with an additional  
 $\init$ transition that initialises all the variables to those defined
 by the initial valuation $\val{0}{C}$ of $C$, 2)~define a pNet action algebra that associates, as action parameter, an
-additional Boolean value to each port, \add{3)~for each exported variable $x$, create the corresponding fresh variable $?x'$ to allow updates during interactions,} 4)~create pNet transitions that reflect the original transitions of
+additional Boolean value to each port, \add{3)~for each exported
+variable $x$, create the corresponding fresh input variable $?x'$ to allow updates during interactions,} 4)~create pLTS transitions that reflect the original transitions of
 $C$ with $\true$ as parameter and 5)~create additional loop transitions marked by
@@
 \item $s_0 \not\in Q_C$ is fresh and $S = Q_C \cup \{s_0\}$,
+  \noteEM{En principe les $vars(s)$ devraient etre disjoints, mais je
+    veux bien laisser ca sous le tapis tant qu'on n'implemente pas le codage...}
 \item $\vars(s) = V_C \cup \setdef{?x'}{x \in \export[C](p), p \in a, s\goesto{a} }$, for all $s \in Q_C$, and $\vars(s_0) =
@@
 \item denoting  $\mathit{init} \bydef{=} \bigl(x := \val{0}{C}(x)\bigr)^{x \in V_C}$ and,
-  \noteSB{Ludo, Eric, pourriez-vous v\'erifier que cela est compr\'ehensible ?}%
+  \noteSB{Ludo, Eric, pourriez-vous v\'erifier que cela est
+    compr\'ehensible ? Ok pour moi (Eric)}%
   \add{for $s \goesto{a, g, u} s'$ with $u = (x := e_x)^{x
@@
 %
+\noteEM{j'ai inverse les $\export[C]'(a), \export[C](a)$ dans les
+  actions, pour etre conforme a la notation de la Def 1 page 4. }
 \begin{multline*}
     {\goesto[{\nopri[C]}]{}} \bydef{=} 
-    \Setdef{\Tuple{s, a\bigl(\export[C](a), \export[C]'(a),\true\bigr), g, u', s'}}{
+    \Setdef{\Tuple{s, a\bigl(\export[C]'(a), \export[C](a),\true\bigr), g, u', s'}}{
       s \goesto{a, g, u} s'}
@@
     {} \cup
-    \Setdef{\Tuple{s, a\bigl(\export[C](a), \export[C]'(a),\false\bigr), \true, \noop, s}}{
+    \Setdef{\Tuple{s, a\bigl(\export[C]'(a), \export[C](a),\false\bigr), \true, \noop, s}}{
       s \in Q_C, \exists s' \in Q_C: s' \goesto{a}}
@@
 by an additional loop transition.
+
+\noteEM{Je m'arrete la, j'\'etais suppos\'e passer apr\`es Simon... (;-)}
 
@@
 \label{secn:conclusion}
+
+What have we done.
 

### 2019-02-16 2018-Arch-pNets/arch-pNets.tex
Derniere pour aujourd'hui

@@
 \medskip
+
+Here is the code of the corresponding composed pNet:
 \noteEMin{Il faudrait (mais a-t-on le temps?): faire un dessin de la
@@
 
-  J'ai une version simplifiee de cet automate ci-dessous.
-
-  Ecrire les proprietes qu'il verifie... ? }
-
-Here is the code of the corresponding composed pNet:
+  Ecrire les proprietes qu'il doit verifier... ? }
 
@@
 
+Fig. \ref{schema:ArchFailure:OA-TimerV4X2} shows the open automata of
+this composed architecture.
+Note that e..g. the open transition labelled ``$fail(*,tt)$'' stands for
+``$fail(b01,b02)$'', where  $b01'$ can be arbitrarily true or
+false. As in the previous case, this is because we have not use here
+the Max Progress hypothesis, otherwise all the ``*'' in the figure
+should be replaced by ``$ff$''.
+
   \begin{figure}[h]

### 2019-02-18 2018-Arch-pNets/arch-pNets.tex
sectino 4 et annexes

@@
 
-\noteEM{Je m'arrete la, j'\'etais suppos\'e passer apr\`es Simon... (;-)}
-
 \Fig{FailureTimer:pNet} shows the encoding of the Failure Monitor
@@
   \includegraphics[width=0.9\columnwidth]{FailureTimerPNET-v4}
-  \caption{The open pNET encoding the Failure Monitor architecture (\fig{schema:ArchFailure:BIP}) without the priority model}
+  \caption{The open pNET encoding the Failure Monitor architecture (\fig{schema:ArchFailure:BIP}) without the Max Progress priority model}
   \label{fig:FailureTimer:pNet}
@@
 %
-  A legitimate question is whether we actually need to do this,
-  instead of listing explicitly the individual interactions, then
-  associating a synchronisation vector to each one of them?  One of
-  the factors is the encoding pNets$\rightarrow$SAT: is it better to
-  have more or fewer SVs if the price is additional Boolean variables?
-  The other factor might be the facility of maximal progress
-  encoding\mdash TBC.  Traceability.  Anything else?\newline
-  \hl{UPDATE: Maximal progress encoding requires this!}
-%
+%%   A legitimate question is whether we actually need to do this,
+%%   instead of listing explicitly the individual interactions, then
+%%   associating a synchronisation vector to each one of them?  One of
+%%   the factors is the encoding pNets$\rightarrow$SAT: is it better to
+%%   have more or fewer SVs if the price is additional Boolean variables?
+%%   The other factor might be the facility of maximal progress
+%%   encoding\mdash TBC.  Traceability.  Anything else?\newline
+%%   \hl{UPDATE: Maximal progress encoding requires this!}
+%% %
 } Indeed, as illustrated by the Failure Monitor architecture in
@@
   the global actions of the synchronisation vectors, simplifying the
-  translation of properties to be verified (\cf \secn{arch:verif}).}
+  translation of properties to be verified (\cf \app{properties}).}
 
@@
 
+\noteEM{Dans le paragraph precedent, tu resume le cas des connecteurs sans data, dans les prochains, tu formalise avec data, mais pour le lecteur ``casual'', le changement n'est pas evident... }
 Below, we assume that, as in \fig{schema:ArchFailure:BIP}, the
@@
 Then, in the SV guard, we have to check whether \emph{all ports
-  leading to $p$ in the caual tree $\tau(x)$ can be fired} (see
+  leading to $p$ in the causal tree $\tau(x)$ can be fired} (see
 \app{transformations}).  If so, then $p$ must be fired, \ie
@@
    [(:hb_B=fail(b0:sva_SV0)
-     /\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
-     /\((resume(false))=(resume(b2:sva_SV1:1:2)))
-     /\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],   {}
+     /\((cancel(false))=(cancel(b1:sva_SV1)))
+     /\((resume(false))=(resume(b2:sva_SV1)))
+     /\(b1:sva_SV1=b2:sva_SV1)],   {}
 OT4 ------------------------------------------------------------
@@
   \begin{equation*}
-    \AG \bigl(\PortFail(true) \rightarrow \EU[]{\lnot \PortFail(true)}{(\PortResume(true) \lor \PortReset)}\bigr).
+    \AG \bigl(\PortFail(true) \rightarrow \EU[]{\lnot \PortFail(true)}{\PortReset}\bigr).
   \end{equation*}
@@
 state 11 where you need another $\PortFail(true)$ before enabling a
-resume (or reset). This is because without priorities we can have an
+reset. This is because without priorities we can have an
 activity on the dandling ``fail'' port without synchronising with the
@@
 - Transition: t1---timeout-->t1, [t in z], { t := 0 z := TopInt}
-pLTS: Failure
+pLTS: Control
 - Transition: s0---init-->s1, { zone := minZone,maxZone}
@@
   correct, montre 37 OTs, modulo les petites questions de mon mail de
-  mercredi midi...
-
-  Ecrire les proprietes qu'il doit verifier... ? }
+  mercredi midi...}
+
+\todoSBin{Ecrire les proprietes qu'il doit verifier... ? }
 
@@
 
+\bigskip
 Fig. \ref{schema:ArchFailure:OA-TimerV4X2} shows the open automata of
@@
   \centering
-  \includegraphics[width=\columnwidth]{TimerV4X2}
+  \includegraphics[width=0.8\columnwidth]{TimerV4X2}
   \caption{The open Automaton of the composed system}

### 2019-02-19 2018-Arch-pNets/arch-pNets.tex
polished and shortened first page of sec 4

@@
 
-We will define the encoding of BIP architectures into pNets by
+We  define the encoding of BIP architectures into pNets by
 associating to each architecture $A = \tuple{\cC, V_A, P_A,
@@
 %%   \in \cC} P_C\}$.
-
-For the sake of clarity and conciseness, we define the encoding of $A$
-into pNets without accounting for any priority model (see
-\secn{components}).  Then, we provide a brief sketch of the
-modification necessary to incorporate the implicitly assumed maximal
-progress priority.
-
+For the sake of clarity, we define the encoding  without  any priority model.  Then, we provide a brief sketch of the
+modifications necessary to encode maximal
+progress (implicitly assumed).
 %% %****************************************************************
@@
 %% \label{secn:enc:nopri}
-
 Recall that $\Gamma$ is an interaction model over the interface
@@
 \paragraph{Encoding the coordinators.}
-The encoding of a coordinator $C$ is a pLTS where we: 1)~introduce a
-fresh initial state with an additional  
+The encoding of a coordinator $C$ is a pLTS with: 1)~an
+ initial state and an   
 $\init$ transition that initialises all the variables to those defined
-by the initial valuation $\val{0}{C}$ of $C$, 2)~define a pNet action algebra that associates, as action parameter, an
-additional Boolean value to each port, \add{3)~for each exported
-variable $x$, create the corresponding fresh input variable $?x'$ to allow updates during interactions,} 4)~create pLTS transitions that reflect the original transitions of
-$C$ with $\true$ as parameter and 5)~create additional loop transitions marked by
+by the initial valuation $\val{0}{C}$ of $C$, 2)~an action algebra that matches the actions of the coordinator ports but adds, an additional boolean action parameter, and also, for each exported
+variable $x$, a corresponding fresh input variable $?x'$ to allow updates during interactions, 3)~pLTS transitions that reflect the original transitions of
+$C$ with $\true$ as parameter and 5)~additional loop transitions marked by
 $\false$.
-
+\noteLH{enleve le 3 et integre au 2}
 Formally,  $\nopri[C] \bydef{=} \pNetTuple{S, s_0, \goesto[{\nopri[C]}]{}}$, such that
@@
 
-\item denoting  $\mathit{init} \bydef{=} \bigl(x := \val{0}{C}(x)\bigr)^{x \in V_C}$ and,
+\item let  $\mathit{uinit} \bydef{=} \bigl(x := \val{0}{C}(x)\bigr)^{x \in V_C}$ and,
   \noteSB{Ludo, Eric, pourriez-vous v\'erifier que cela est
-    compr\'ehensible ? Ok pour moi (Eric)}%
-  \add{for $s \goesto{a, g, u} s'$ with $u = (x := e_x)^{x
-    \in V}$ (for some $V \subseteq V_C$),
-%  
-  $u' \bydef{=}
+    compr\'ehensible ? Ok pour moi (Eric) OK Ludo, rephrase un peu}%
+  \add{for all $s \goesto{a, g, u} s'$ with $u = (x\! :=
+\! e_x)^{x
+    \in V}$ (with $V \!\subseteq\! V_C$),
+%  
+  let $u' \bydef{=}
   \bigl(x := e_x\bigr)^{x \in V \setminus \export[C](a)}
@@
     \\
-    {} \cup \bigl\{(s_0, \init, \true, \mathit{init}, q^0_C)\bigr\}.
+    {} \cup \bigl\{(s_0, \init, \true, \mathit{uinit}, q^0_C)\bigr\}.
   \end{multline*}}
-\end{itemize}
+\end{itemize}\vspace{-3ex}
 
@@
 vector must participate in the synchronisation.  To address this
-difference, we use the classical~\cite{milner83-calculi} approach,
-whereby non-participation of a port in an interaction is simulated
-by an additional loop transition.
+difference, we use the classical approach
+where non-participation of a port in an interaction is simulated
+by an additional loop transition~\cite{milner83-calculi}.
 

### 2019-02-19 2018-Arch-pNets/arch-pNets.tex
conclusion : Eric + Ludo

@@
 variable $x$, a corresponding fresh input variable $?x'$ to allow updates during interactions, 3)~pLTS transitions that reflect the original transitions of
-$C$ with $\true$ as parameter and 5)~additional loop transitions marked by
+$C$ with $\true$ as parameter and 4)~additional loop transitions marked by
 $\false$.
@@
 \PortReset\}\bigr\}$.  This corresponds to the intuition that the
-dangling ports {\PortFail} and {\PortResume} will be provided by a 
+dangling ports {\PortFail} and {\PortResume} will be provided by a \noteLH{monitored ou monitoring???}
 monitored component, whereas {\PortAsk} and {\PortReset} correspond to
@@
 
-What have we done.
-
-Discussion:
-
-- what did we lern about comparison of the coordination models ?
-
-- extension to other priority features
-
-- proof of correctness ?
+BIP architectures are composition tools that enforce safety properties; the composition of architectures entails the composition of the associated properties.
+We have extended architectures with data-sensitive interactions, and proved that this extension still guarantees the preservation of safety properties by architecture composition, under reasonable assumptions.
+This extends the original compositional methodology offered by BIP architectures.
+Then we use pNets as a semantic formalism to encode architectures with data.
+pNet is a low level coordination model for open systems, in which composition preserves bisimulation equivalences.
+pNet is equipped with tools computing its behavioural semantics in terms of symbolic automata, allowing model-checking and equivalence checking with algorithms relying on SMT engines.
+As a result, we obtain automatic and compositional guarantees of safety properties with data where compositionality is given by the BIP architectures, and pNet tools provide automatic verification of the properties of each architecture.
+%
+%The automatic checking of properties given by the pNet framework
+%
+%Discussion…:
+%-	What did we learn about comparison of the coordination models ? Worth mentioning architectures are flat, so we don’t use the power of hierschical pNets (as providinh=g encapsulation mechanism) ?
+%-	What about liveness, fairness ?
+%-	Extension to other kind of priorities ?
+%-	Shall we make a full proof of correctness of the encoding?
+%-	Tooling = implementation of the encoding from BIP arch editing tools + tracing back verification diagnoses to the BIP level.
+%
+%
+%What have we done.
+%
+%Discussion:
+%
+%- what did we lern about comparison of the coordination models ?
+%
+%- extension to other priority features
+%
+%- proof of correctness ?
 

### 2019-02-19 2018-Arch-pNets/arch-pNets.tex
arch-pNets paper: Fixed a bug in Fig 1 (fail |--> {zone}, instead of reset |--> {zone})
eric comments

@@
 We provide a solution for the design of safe concurrent systems by
-compositional application of verified design patterns\mdash which we
-call \emph{architectures}\mdash to a \noteEM{ca veut dire quoi, minimal? On enleve ?}minimal set of functional
+compositional application of verified design patterns\mdash 
+called \emph{architectures}\mdash to a small set of functional
 components.  To this end, we extend the theory of architectures
@@
 
-\keywords{Verification, \noteEM{Je mettrais bien symbolic quelque part...}symbolic automaton, composition, safety, interaction
+\keywords{Symbolic verification, composition, safety, interaction
   models.}
@@
 mechanisms of the two models but also the way component composition is
-expressed in the two formalisms. \noteEM{J'ai vire une phrase un peu
-  redondante avec la phrase precedente, et deja une autre 20 lignes
-  plus haut... }
+expressed in the two formalisms. 
 %This also gives the opportunity
@@
 \renewcommand{\Post}{u}
-The semantics of an open pNet is expressed as  an automaton where each transition \noteEM{remplacer composes par ``coordinates'' ?}composes the actions of several holes, 
+The semantics of an open pNet is expressed as  an automaton where each transition coordinates the actions of several holes, 
 the transition occurs if some predicates hold, and can involve  
@@
 Previous works on pNets and BIP architectures have been mentioned at the beginning of the paper.
-Consequently, we  review here the closest related works outside the scope of pNets and BIP architectures.
-Among those, we focus on existing approaches for the compositional and parameterized verification of systems, and on alternative verification engines???
-\noteLH{not sure about this classification ; to be refined}
+We  review here the closest related works outside the scope of pNets and BIP architectures, with a particular focus on compositional and parameterized verification.
 
@@
 %%% compositional verification
-approaches by typing interfaces/protocols == Simon
+%approaches by typing interfaces/protocols == Simon
 
@@
 models suitable for compositional verification.
-
 Among these works, several have shown the capacity of the SMT engines
@@
 the algorithms, for large case-studies
-(e.g. \cite{DBLP:journals/corr/CimattiGMT13,DBLP:journals/corr/abs-1806-11459}).
+(e.g. \cite{DBLP:journals/corr/CimattiGMT13,DBLP:journals/corr/abs-1806-11459}). Also 
 %% SMT on an application not using component structure. is there a strong Z3 example == Eric
@@
 As compositional proof of safety is difficult, some approaches rely on theorem proving to ensure the safety of component operations.
-Coqots and Pycots\cite{BCDLM:CBSE2014} even allow to prove the safety of reconfiguration procedures which are known to be highly difficult to verify, and massively parametrised.
-unfortunately the approach relies on a high expertise and significant efforts from the component user as (s)he must prove manually the safety of the reconfiguration process.
-In this paper, we rely on automatic encoding into a SMT solver making the proof of properties much more automatic, but we cannot prove the safety of the reconfiguration procedure.
+Coqots and Pycots~\cite{BCDLM:CBSE2014} even manage to prove the safety of reconfiguration procedures which are known to be highly difficult to verify, and massively parametrised.
+The approach relies on a high expertise and significant efforts from the user.
+Here, we rely on automatic verification thanks to the SMT solver but we cannot prove the safety of the reconfiguration procedure.
 
 In~\cite{DDJO:JLAMP2012}, the authors propose a compositional proof system for distributed objects that is suitable for implementation within the KeY framework~\cite{BHS:Key2007} and uses a Hoare logic approach.
-The approach relies on history invariant for each object, separating local reasoning for proving object invariant from global reasoning that relies on well-formedness of traces.
-Compared to this  approach, we do not  deal with complex history-based specifications because we use interaction specification and SMT-reasoning instead of Hoare logic.
-Also the correctness of the composition is given by the properties of architectures which allows for more flexibility than well-formedness of traces.
+%The approach relies on history invariant for each object, separating local reasoning for proving object invariant from global reasoning that relies on well-formedness of traces. 
+Compared to this  approach, we do not  deal with complex history-based specifications and use interaction specification and SMT-reasoning instead of Hoare logic. 
+%Also the correctness of the composition is given by the properties of architectures which allows for more flexibility than well-formedness of traces.
 

### 2019-02-19 2018-Arch-pNets/arch-pNets.tex
Small comments and new paragraph

@@
 }$
-\noteEM{Attention, bug dans la figure 2, ou tu mets $reset\mapsto \mathit{zone}$}{respectively}.
+\noteEM{Attention, bug dans la figure 2, ou tu mets $reset\mapsto \mathit{zone}$}\noteSB{Done!}respectively.
 %
@@
   translation of properties to be verified (\cf \app{properties}).}
-
-The general case encoding relies on the causal semantics of the
+\noteLH{ce paragraphe sonne vraiment note de rapport de recherche, tu arrives a lui donner un peu d'abstraction/de recul?}
+
+In the general case, the encoding relies on the causal semantics of the
 algebra of BIP connectors \cite{BliSif10-causal-fmsd}.  Disregarding
@@
 
-\bigskip
+\paragraph{Maximal progress.}
 In order to encode the maximal progress priority model, one has to

### 2019-02-19 2018-Arch-pNets/arch-pNets.tex
arch-pNets paper: Reshuffled appendices; merged sections 4 and 5 and added a paragraph to the end of section3

--- 2019-02-19 2018-Arch-pNets/arch-pNets.tex
@@
 \newcommand{\thm}[1]{Th.~\ref{thm:#1}}
+\newcommand{\Thm}[1]{Theorem~\ref{thm:#1}}
 \newcommand{\axs}[1]{Ax.~\ref{ax:#1}}
@@
 
+\addSB{%
+%
+\Thm{combining} implies that safe BIP systems can be designed
+\emph{compositionally}.  Indeed, it is sufficient to verify that
+1)~the applied architectures do enforce their characteristic
+properties and 2)~that they are pairwise upwards compatible.  To
+a large extent, item~2, \ie verification of the upwards
+compatibility, can be carried out syntactically by analysing the
+structure of the connectors defining the interaction models:
+maximal progress is mostly relevant for connectors involving
+triggers; whenever a trigger port is not common to both
+architectures, upwards \emph{in}compatibility cannot arise.  The
+next section is devoted to the encoding of architectures into
+pNets, which addresses item~1 by symbolic verification.
+%
+}
+
 %****************************************************************
-
 %****************************************************************
@@
 The encoding of the interaction model is based on its representation
-as a set of connectors. \noteSB{%
+as a set of connectors. %% \noteSB{%
 %
@@
 %% %
-} Indeed, as illustrated by the Failure Monitor architecture in
+%% }
+Indeed, as illustrated by the Failure Monitor architecture in
 \fig{schema:ArchFailure:BIP}, each connector can define several
@@
 
-\bigskip
-In order to encode the maximal progress priority model, one has to
-introduce an additional Boolean variable, for each port, for which we
-have introduced one in $\nopri[A, \partition]$.  Intuitively, the
-variables introduced above determine whether the original transition
-labeled by the port is executed (\true), or rather the corresponding
+\paragraph{Encoding of the maximal progress priority model}
+We only present the key idea, which consists in
+introducing an additional Boolean variable, for each port, for which we
+have introduced one in $\nopri[A, \partition]$.  Intuitively, 
+the Boolean
+variables introduced for the encoding of interaction models
+determine whether it is the original transition
+labeled by the port that is executed (\true), or rather the corresponding
 self-loop, introduced by the encoding (\false).  The new variables
@@
 \app{transformations}).  If so, then $p$ must be fired, \ie
-$p(\false)$ must be blocked.  %% This is pretty much straightforward, but
+$p(\false)$ must be blocked.
+%% This is pretty much straightforward, but
 %% care must be taken when doing this in the general case, since causal
@@
 
-\section{Case study}
-\label{secn:case-study}
-
-%****************************************************************
+%% \section{Case study}
+%% \label{secn:case-study}
+
+%% %****************************************************************
 
@@
 
-%****************************************************************
-
-\subsection{Composition of architectures}
-\label{secn:arch:composition}
-
-We now consider a system comprising two components $B_1$ and $B_2$
-with the corresponding interfaces $\tuple{V_i, P_i,
-  \export[i]}_{i=1,2}$, such that $\listset{\PortFail_i,
-  \PortResume_i} \subseteq P_i$, for $i = 1,2$.
-
-Assuming that the associated system requirements comprise the
-capability of monitoring the failure events corresponding to ports
-$\PortFail_1$ and $\PortFail_2$ of the two components, we would like
-to apply two instances of the Failure Monitor architecture.  However,
-we impose an additional constraint: only one timer coordinator is
-allowed, for example because it must eventually be implemented by a
-hardware component.
-
-We consider two architecture instances $A_i = \tuple{\cC_i, V_{A_i},
-  P_{A_i}, \export[A_i], \Gamma_i}$, for $i = 1,2$, with all their
-constituting elements cloned from the Failure Monitor architecture of
-the previous examples while substituting each entity $X$ by $X^i$.
-For instance, the initialisation of the $\mathit{zone}$ variable is
-transformed into $\IntervalInit[1]$ and $\IntervalInit[2]$,
-respectively.  The only exception to this cloning procedure are the
-sets of coordinating components: $\cC^i = \listset{\NameTimer,
-  \NameCtrl^i}$, \ie the $\NameTimer$ component is shared, while
-components $\NameCtrl^1$ and $\NameCtrl^2$ are obtained by making two
-copies of $\NameCtrl$ as above.
-
-In order to apply both architectures, we must verify that they are
-upwards compatible and compute the combined interaction model $\Gamma$
-in $A_1 \arcomp A_2 = \tuple{\cC_1 \cup \cC_2, V_{A_1} \cup V_{A_2},
-  P_{A_1} \cup P_{A_2}, \export[A_1] \cup \export[A_2], \Gamma}$
-(see \defn{arch:composition}).
-
-\todoSBin{Complete this section}
+%% %****************************************************************
+
+%% \subsection{Composition of architectures}
+%% \label{secn:arch:composition}
+
+%% We now consider a system comprising two components $B_1$ and $B_2$
+%% with the corresponding interfaces $\tuple{V_i, P_i,
+%%   \export[i]}_{i=1,2}$, such that $\listset{\PortFail_i,
+%%   \PortResume_i} \subseteq P_i$, for $i = 1,2$.
+
+%% Assuming that the associated system requirements comprise the
+%% capability of monitoring the failure events corresponding to ports
+%% $\PortFail_1$ and $\PortFail_2$ of the two components, we would like
+%% to apply two instances of the Failure Monitor architecture.  However,
+%% we impose an additional constraint: only one timer coordinator is
+%% allowed, for example because it must eventually be implemented by a
+%% hardware component.
+
+%% We consider two architecture instances $A_i = \tuple{\cC_i, V_{A_i},
+%%   P_{A_i}, \export[A_i], \Gamma_i}$, for $i = 1,2$, with all their
+%% constituting elements cloned from the Failure Monitor architecture of
+%% the previous examples while substituting each entity $X$ by $X^i$.
+%% For instance, the initialisation of the $\mathit{zone}$ variable is
+%% transformed into $\IntervalInit[1]$ and $\IntervalInit[2]$,
+%% respectively.  The only exception to this cloning procedure are the
+%% sets of coordinating components: $\cC^i = \listset{\NameTimer,
+%%   \NameCtrl^i}$, \ie the $\NameTimer$ component is shared, while
+%% components $\NameCtrl^1$ and $\NameCtrl^2$ are obtained by making two
+%% copies of $\NameCtrl$ as above.
+
+%% In order to apply both architectures, we must verify that they are
+%% upwards compatible and compute the combined interaction model $\Gamma$
+%% in $A_1 \arcomp A_2 = \tuple{\cC_1 \cup \cC_2, V_{A_1} \cup V_{A_2},
+%%   P_{A_1} \cup P_{A_2}, \export[A_1] \cup \export[A_2], \Gamma}$
+%% (see \defn{arch:composition}).
+
+%% \todoSBin{Complete this section}
 
@@
 
-%****************************************************************
-%****************************************************************
-
-\section{Proofs}
-\label{secn:proofs}
-
-\begin{lemma}
-  \label{lem:onlyone}
-  Let $A = \tuple{\cC, V_A, P_A, \export[A], \Gamma}$ be an architecture and denote
-  by $\Gamma_\cC \bydef{=}
-%
-  \setdef{
-    (a \cap P_\cC, \true, \noop)
-  }{
-    (a, g, e) \in \Gamma
-  }$, with $P_\cC = \bigcup_{C \in \cC} P_C$,
-%  
-  the projection of $\Gamma$ onto the coordinating components of
-  $A$.  Consider the architecture $A' = \tuple{\{C'\}, V_A, P_A, \export[A],
-  \Gamma}$, where $C' = \Gamma_\cC(\cC)$.  For any set of
-  components $\cB$, satisfying the conditions of
-  \defn{arch:application}, we have
-  $\semopen{A(\cB)} = \semopen{A'(\cB)}$.
-\end{lemma}
-%
-\begin{proof}
-  First of all, notice that, by \defn{im:sem},
-  $V_{C'} = \bigcup_{C \in \cC} V_C$ and $P_{C'} = P_\cC = \bigcup_{C \in \cC} P_C$.
-  The conditions of \defn{arch} are satisfied and $A'$ is indeed
-  an architecture.  Furthermore, $\cB$ satisfies the conditions
-  of \defn{arch:application} \wrt $A'$.  Hence, the component
-  $A'(\cB)$ is well defined.
-
-  Clearly the state spaces and initial states %% and interfaces
-  of both LTSs $\semopen{A(\cB)}$ and $\semopen{A'(\cB)}$
-  coincide.  Thus, we only have to prove that so do the
-  transition relations.  Let us assume that
-  $\cC = C_i^{i \in I}$ and $\cB = B_j^{j \in J}$.
-  We will use $q_i, q_i'$ to denote the states of
-  $C_i$ and $q_j, q_j'$ to denote the states of $B_j$,
-  and similarly for the valuations of variables.
-
-  By \defn{comp:semantics},
-%
-  \begin{equation}
-    \label{eq:lem1:trans:sem}
-    (q_i, \val{}{i})^{i \in I} (q_j, \val{}{j})^{j \in J}
-    \goesto{a, \val[\tilde]{}{}}
-    (q_i', \val{\prime}{i})^{i \in I}
-    (q_j', \val{\prime}{j})^{j \in J}
-  \end{equation}
-%  
-  is a transition in $\semopen{A(\cB)}$ (\resp
-  $\semopen{A'(\cB)}$) iff
-%
-  \begin{equation}
-    \label{eq:lem1:trans}
-    q_i^{i \in I} q_j^{j \in J}
-    \goesto{a, g', e'}
-    (q_i')^{i \in I} (q_j')^{j \in J}
-    \,,
-  \end{equation}
-%
-  is a transition in $A(\cB)$ (\resp $A'(\cB)$) and
-%
-  \begin{mathpar}
-    \val{i \in I}{i} \val{j \in J}{j}
-    \models g'
-    \,,
-    \and
-    (\val{\prime}{i})^{i \in I} (\val{\prime}{j})^{j \in J}
-    = \val[\tilde]{}{}[e']
-    \,,
-    \and
-    \valdiff{\val{i \in I}{i} \val{j \in J}{j}}{
-      \val[\tilde]{}{}} \subseteq \export(a)       
-  \end{mathpar}
-%
-  (with $\export$ defined as in \defn{arch:application}).
-
-  By \defn{im:sem} and \defn{priority:sem}, \eq{lem1:trans} is a transition in $A(\cB)$
-  iff $a \neq \emptyset$, $(a, g, e) \in \IMextend{\Gamma}{P}$,
-  where $P = \bigcup_{B \in \cB \cup \cC} P_B$, and
-  %
-  \begin{enumerate}
-  \item\label{ab:start} for $i \in I$,\\
-    $a \cap P_{C_i} \neq \emptyset$ and
-    $q_i \goesto{a \cap P_{C_i},\, g_{C_i},\, e_{C_i}} q_i'$
-    is a transition in $C_i$, or\\
-    $a \cap P_{C_i} = \emptyset$ and $q_i = q_i'$
-    (for covenience, we put $g_{C_i} = \true$ and $e_{C_i} = \noop$ in item~\ref{aux1} below);
-  \item for $j \in J$,\\
-    $a \cap P_{B_j} \neq \emptyset$ and
-    $q_j \goesto{a \cap P_{B_j},\, g_{B_j},\, e_{B_j}} q_j'$
-    is a transition in $B_j$, or\\
-    $a \cap P_{B_j} = \emptyset$ and $q_j = q_j'$
-    (for covenience, we put $g_{B_j} = \true$ and $e_{B_j} = \noop$ in item~\ref{aux1} below);
-  \item\label{ab:end}\label{aux1} $g' = g \land \bigwedge_{i \in I} g_{C_i} \land
-    \bigwedge_{j \in J} g_{B_j} \land \varphi_\mu$ and
-    $e' = e; e_{C_i}^{i \in I}, e_{B_j}^{j \in J}$, where    
-%
-    \begin{equation}
-      \label{eq:only1:maxprog:guard}
-      \varphi_\mu = \bigwedge_{
-        \begin{array}{c}
-          q_i^{i \in I} q_j^{j \in J} \goesto{b, h, f} \text{ in }
-          (\IMextend{\Gamma}{P})(\cC \cup \cB)
-          \\
-          a \varsubsetneq b
-        \end{array}
-      } \lnot h
-      \,.
-    \end{equation}
-%
-  \breakenumistart
-
-  Similarly, \eq{lem1:trans} is a transition in
-  $A'(\cB)$ iff $a \neq \emptyset$,
-  $(a, g, e) \in \IMextend{\Gamma}{P}$ and
-%
-  \breakenumiend
-% 
-  \item \label{a1b:start} \label{only1:coord}
-    $a \cap P_{C'} \neq \emptyset$ and 
-    $(q_i)^{i \in I} \goesto{a \cap P_{C'}, g_{C'}, e_{C'}} (q_i')^{i \in I}$
-    is a transition in $C'$, or\\
-    $a \cap P_{C'} = \emptyset$ and $q_i = q_i'$,
-    for all $i \in [1,m]$
-    (for covenience, we put $g_{C'} = \true$ and $e_{C'} = \noop$ in
-    item~\ref{aux2} below);
-  \item for $j \in J$,\\
-    $a \cap P_{B_j} \neq \emptyset$ and
-    $q_j \goesto{a \cap P_{B_j}, g_{B_j}, e_{B_j}} q_j'$
-    is a transition in $B_j$, or\\
-    $a \cap P_{B_j} = \emptyset$ and $q_j = q_j'$
-    (for covenience, we put $g_{B_j} = \true$ and $e_{B_j} = \noop$ in
-    item~\ref{aux2} below);
-  \item\label{aux2} $g' = g \land g_{C'} \land
-    \bigwedge_{j \in J} g_{B_j} \land \varphi_\mu'$ and
-    $e' = e; e_{C'}, e_{B_j}^{j \in J}$ (with $\varphi_\mu'$ defined as
-    in \eq{only1:maxprog:guard}, but substituting $\{C'\}$ instead of $\cC$).
-%
-  \breakenumistart
-  Notice that, for any $i \in I$, since
-  $P_{C_i} \subseteq P_{C'}$, we have
-  $a \cap P_{C_i} = (a \cap P_{C'}) \cap P_{C_i}$.
-  Thus, if $a \cap P_{C'} \neq \emptyset$, 
-  the transition in condition~\ref{only1:coord} above is
-  present in $C'$ iff
-  $(a \cap P_{C'}, \true, \noop) \in \Gamma_\cC$ and
-  \breakenumiend
-% 
-  \item for $i \in I$,\\
-    $a \cap P_{C_i} \neq \emptyset$ and
-    $q_i \goesto{a \cap P_{C_i}, g_{C_i}, e_{C_i}} q_i'$
-    is a transition in $C_i$, or\\
-    $a \cap P_{C_i} = \emptyset$ and $q_i = q_i'$,
-    (for covenience, we put $g_{C_i} = \true$ and $e_{C_i} = \noop$ in
-    item~\ref{aux3} below);
-  \item \label{a1b:end} \label{aux3} $g_{C'} = \bigwedge_{i \in I} g_{C_i}$ and
-    $e_{C'} = e_{C_i}^{i \in I}$.
-  \end{enumerate}
-
-  Consider $(a,g,e) \in \IMextend{\Gamma}{P}$.  By
-  \defn{arch:application}, this is equivalent to
-  $(a \cap P_A, g, e) \in \Gamma$.
-  Since $P_{C'} = P_\cC \subseteq P_A$, we have
-  $a \cap P_{C'} = a \cap P_\cC = (a \cap P_A) \cap P_\cC$.
-  Hence, by the definition of $\Gamma_\cC$ in the lemma statement,
-  this is also equivalent to
-  $(a \cap P_{C'}, \true, \noop) \in \Gamma_\cC$.
-
-  Thus, conditions \ref{ab:start}\ndash\ref{ab:end} are satisfied iff
-  so are conditions \ref{a1b:start}\ndash\ref{a1b:end} (to see that
-  $\varphi_\mu$ is satisfied iff so is $\varphi_\mu'$, one has to
-  consider the same two sets of conditions, but this time without the
-  additional conjuncts $\varphi_\mu$ and $\varphi_\mu'$ in
-  items~\ref{aux1} and \ref{aux2}, since no priority model is applied
-  to obtain $C'$).  This proves that the transition relations of
-  $\semopen{A(\cB)}$ and $\semopen{A'(\cB)}$ coincide and, therefore,
-  $\semopen{A(\cB)} = \semopen{A'(\cB)}$.
-\end{proof}
-
-\begin{note}
-  \label{rem:upwards:compat}
-  Notice that, since, in the statement of \lem{onlyone}, 
-  %
-  \begin{enumerate}
-  \item the interaction models are the same for both $A$ and $A'$, and
-  \item $P_{C'} = P_\cC$,
-  \end{enumerate}
-  %
-  substituting $A'$ for $A$ preserves upwards compatibility, \ie for any
-  architecture $A''$, holds the following statement: $A$ and $A''$ are
-  upwards compatible if and only if so are $A'$ and $A''$.
-\end{note}
-
-\begin{lemma}
-  \label{lem:onestep}
-  Let $\cB$ be a set of components; let $A_i = \tuple{\{C_i\}, V_{A_i},
-  P_{A_i}, \export[A_i], \Gamma_i}$, for $i = 1,2$, be two upwards compatible architectures
-  with one coordinator each, applicable to $\cB$.  Denote
-  $P_i = P_{C_i} \cup \bigcup_{B \in \cB} P_B$.
-  Finally, let
-%
-  $
-  s_1 s_2 s
-%
-  \goesto{a, \tilde{\val{}{}}}
-%
-  s_1' s_2' s'
-  $,
-%
-  be a transition in $\semopen{(A_1 \arcomp A_2)(\cB)}$, with
-  $a \neq \emptyset$, 
-  $s, s' \in \prod_{B \in \cB} S_{\semopen{B}}$
-  and
-  $s_i, s_i' \in S_{\semopen{C_i}}$ ($i=1,2$).
-%
-  Then, for $i=1,2$, either $a \cap P_i = \emptyset$ and $s_i s=
-  s_i' s'$, or there exists a transition
-%
-  $
-  s_i s
-%
-  \goesto{a \cap P_i, \val[\doubletilde]{}{}}
-%
-  s_i' s''
-  $ 
-%
-  in $\semopen{A_i(\cB)}$, with
-  $\val[\doubletilde]{}{}$ being the restriction of
-  $\val[\tilde]{}{}$ to
-  $V_i = V_{C_i} \cup \bigcup_{B \in \cB} V_B$ and
-  $s' \order s''$.
-\end{lemma}
-%
-\begin{proof}
-  By \defn{comp:semantics}, every semantic state consists of a
-  component state and a valuation of component variables.  Thus,
-  we can expand $s_1 s_2 s \goesto{a, \tilde{\val{}{}}} s_1' s_2' s'$
-  as
-%
-  \[
-  (q_1, \val{}{1}, q_2, \val{}{2}, q, \val{}{})
-%
-  \goesto{a, \tilde{\val{}{}}}
-%
-  (q_1', \val[\primeit]{}{1}, q_2', \val[\primeit]{}{1}, q', \val[\primeit]{}{})
-  \,.
-  \]
-%
-  By \defn{im:sem} and \defn{priority:sem}, this implies
-  that
-  $(q_1, q_2, q) \goesto {a, g', e'} (q_1', q_2', q')$
-  is a transition in $(A_1 \arcomp A_2)(\cB)$, with
-%
-  $g' = g \land g_1 \land g_2 \land g_\cB \land \varphi_\mu$
-  and
-  $e' = e; (e_1, e_2, e_\cB)$,
-  where $(a, g, e) \in \Gamma$ (see \eq{arch:composition} for the
-  definition of $\Gamma$);
-%  
-  $g_1$, $g_2$ and $e_1$, $e_2$ are, respectively, the guards and
-  update expressions of the underlying transitions in the coordinating
-  components $C_1$ and $C_2$;
-%    
-  \begin{mathpar}
-    g_\cB = \bigwedge_{B \in \supp{a} \cap \cB} g_B
-    \,,
-    \and
-    e_\cB = e_B^{B \in \supp{a} \cap \cB}
-    \,,
-  \end{mathpar}
-%
-  are the compositions of, respectively, the guards and update
-  expressions of the operand components;
-%    
-  \begin{equation}
-    \label{eq:onestep:maxprog:guard}
-    \varphi_\mu = \bigwedge_{
-      \begin{array}{c}
-        (q_1, q_2, q) \goesto{b, h', f'} \text{ in }
-        \bigl(\IMextend{\Gamma}{(P_1 \cup P_2)}\bigr)
-        \bigl(\{C_1, C_2\} \cup \cB\bigr)
-        \\
-        a \varsubsetneq b
-      \end{array}
-    } \lnot h'
-  \end{equation}
-%
-  is the conjunct encoding the maximal progress priority in
-  \defn{priority:sem}.  As above for $g'$, for each $(b, h', f')$ in
-  \eq{onestep:maxprog:guard}, $h'$ can be decomposed as $h' = h \land
-  h_1 \land h_2 \land h_\cB$ (without the maximal progress conjunct,
-  since no priority is applied in $\bigl(\IMextend{\Gamma}{(P_1 \cup
-    P_2)}\bigr)\bigl(\{C_1, C_2\} \cup \cB\bigr)$).
-
-  By \eq{comp:semantics}, we also have
-%
-  \begin{align}
-    \label{eq:guard}
-    (\val{}{1}, \val{}{2}, \val{}{}) &\models g'
-    \,,
-    \\
-    \label{eq:substitution}
-    (\val[\primeit]{}{1}, \val[\primeit]{}{2}, \val[\primeit]{}{})
-    &= \val[\tilde]{}{}[e']
-    \,,
-    \\
-    \label{eq:transient}
-    \valdiff{(\val{}{1}, \val{}{2}, \val{}{})}{\val[\tilde]{}{}}
-    &\subseteq \export(a)
-    \,.
-  \end{align}
-%
-  If $a \cap P_1 = \emptyset$, then $\supp{a} = \{C_2\}$ and, by
-  \eq{transient} and \defn{im:sem}, $s_1 = s_1'$ and $s = s'$
-  (recall, \defn{im}, that, for $(a,g,e) \in \Gamma$, we have $e
-  \in \exprs{V_a}$).  Hereafter, assume $a \cap P_1 \neq
-  \emptyset$.
-
-  By \eq{arch:composition}, for $i=1,2$, there exist $(a \cap P_{A_i},
-  g^i, e^i) \in \Gamma_i$, such that $g = g^1 \land g^2$ and $e = e^1
-  \land e^2$.
-  %% Similarly, for each $(b, h', f')$ in \eq{onestep:maxprog:guard},
-  %% there exist $(b \cap P_{A_i}, h^i, f^i) \in \Gamma_i$, such that
-  %% $h = h^1 \land h^2$ and $f = f^1 \land f^2$.
-%
-  We want to show that the interaction $(a \cap P_1, g^1, e^1)$ is
-  enabled in the state $(q_1, \val{}{1}, q, \val{}{})$ of
-  $\semopen{A_1(\cB)}$.  To this end, we proceed in two steps:
-%
-  \begin{enumerate}
-  \item \label{onestep:proof:im} We show that $(a \cap P_1, g^1,
-    e^1)$ is enabled in the state $(q_1, \val{}{i}, q, \val{}{})$ of
-    $\semopen{(\IMextend{\Gamma_1}{P_1})(\cB)}$.
-  \item \label{onestep:proof:maxp} We show that $(a \cap P_1, g^1,
-    e^1)$ is not inhibited in $\semopen{A_1(\cB)} =
-    \semopen{\mu\bigl((\IMextend{\Gamma_1}{P_1})(\cB)\bigr)}$ by the
-    maximal progress priority.
-  \end{enumerate}
-
-  \paragraph*{Step \ref{onestep:proof:im}}
-  %% Denoting $P_\cB = \bigcup_{B \in \supp{a} \cap \cB} P_B$, 
-  By \defn{im:sem}, we have
-%
-  \begin{mathpar}
-    q_1 \goesto{a \cap P_{C_1}, g_1, e_1} q_1'
-    \and
-    \text{and}
-    \and
-    q_B \goesto{a \cap P_B, g_B, e_B} q_B',
-    \text{ for each }
-    B \in \cB
-    \,.
-  \end{mathpar}
-
-  By \eq{guard}, we have
-  $(\val{}{1}, \val{}{}) \models g^1 \land g_1 \land g_\cB$.
-
-  Denoting \todoSB{One tilde is enough}$\val[\doubletilde]{}{1}$ the restriction of
-%
-  $\val[\tilde]{}{}$ to
-  $V_1 = V_{C_1} \cup \bigcup_{B \in \cB} V_B$,
-%
-  we have, by \eq{substitution} and the monotonicity of
-  expressions,
-%
-  $(\val[\primeit]{}{1}, \val[\primeit]{}{}) \order
-  \val[\doubletilde]{}{1}[e^1; (e_1, e_b)]$.  \todoSB{Remove this}\hl{Notice that all
-  variables affected by both $e^1$ and $e^2$ must necessarily
-  belong to $\bigcup_{B \in \cB} V_B$.}  Hence,
-%
-  $\val[\doubletilde]{}{1}[e^1; (e_1, e_b)] =
-  (\val[\primeit]{}{1}, \val[\secondit]{}{})$ with 
-  $\val[\primeit]{}{} \order \val[\secondit]{}{}$.
-
-  By \defn{comp:semantics} and \defn{im:sem}, we have
-  $
-  (q_1, \val{}{1}, q, \val{}{})
-  \goesto{a \cap P_1, \val[\doubletilde]{}{1}}
-  (q_1', \val[\primeit]{}{1}, q, \val[\secondit]{}{})
-  $ in $\semopen{(\IMextend{\Gamma_1}{P_1})(\cB)}$.
-
-  Symmetrically, we have 
-  $
-  (q_2, \val{}{2}, q, \val{}{})
-  \goesto{a \cap P_2, \val[\doubletilde]{}{2}}
-  (q_2', \val[\primeit]{}{2}, q, \val[\secondit]{}{})
-  $ in $\semopen{(\IMextend{\Gamma_2}{P_2})(\cB)}$.
-
-  \paragraph*{Step \ref{onestep:proof:maxp}}
-  Suppose that $a \cap P_1 \varsubsetneq b_1$, for some interaction
-  $(b_1, h^1, f^1) \in \IMextend{\Gamma_1}{P_1}$ enabled in $(q_1,
-  \val{}{1}, q, \val{}{})$.  Then, by upwards compatibility of $A_1$
-  and $A_2$, there exists $(b_2, h^2, f^2) \in
-  \IMextend{\Gamma_2}{P_2}$, enabled in $(q_2, \val{}{2}, q,
-  \val{}{})$, such that $a \cap P_2 \subseteq b_2$ and $b_2 \cap P_1 =
-  b_1 \cap P_2$.  By \defn{arch:application}, we have $(b_1 \cap P_{A_1},
-  h^1, e^1) \in \Gamma^1$.  Furthermore,
-%
-  \begin{multline*}
-    ((b_1 \cap P_{A_1}) \cup (b_2 \cap P_{A_2}))  \cap P_{A_1} =
-    (b_1 \cap P_{A_1}) \cup (b_2 \cap P_{A_1} \cap P_{A_2}) =\\
-    (b_1 \cap P_{A_1}) \cup ((b_2 \cap P_1) \cap P_{A_1} \cap P_{A_2}) =  
-    (b_1 \cap P_{A_1}) \cup ((b_1 \cap P_2) \cap P_{A_1} \cap P_{A_2}) =\\
-    (b_1 \cup (b_1 \cap P_2 \cap P_{A_2})) \cap P_{A_1} =
-    b_1 \cap P_{A_1} 
-  \end{multline*}
-%
-  Symmetrically, $(b_2 \cap P_{A_2}, h^2, e^2) \in \Gamma^2$ and
-  $((b_1 \cap P_{A_1}) \cup (b_2 \cap P_{A_2})) \cap P_{A_2} = b_2
-  \cap P_{A_2}$.  By \eq{arch:composition}, we then have $((b_1 \cap
-  P_{A_1}) \cup (b_2 \cap P_{A_2}), h^1 \land h^2, f^1 \expmix f^2)
-  \in \Gamma$ and, by \defn{arch:application}, $(b_1 \cup b_2, h^1 \land
-  h^2, f^1 \expmix f^2) \in \IMextend{\Gamma}{(P_1 \cup P_2)}$.
-%
-  Since both $(b_i, h^i, f^i) \in \IMextend{\Gamma_i}{P_i}$ are
-  enabled in the respective states $(q_i, \val{}{i}, q, \val{}{})$, we
-  conclude that $(b_1 \cup b_2, h^1 \land h^2, f^1 \expmix f^2)$ is
-  enabled in $(q_1, \val{}{1}, q_2, \val{}{2}, q, \val{}{})$.
-
-  Since $a \cap P_1 \varsubsetneq b_1$ and $a \cap P_2 \subseteq b_2$,
-  we have $a \varsubsetneq b_1 \cup b_2$.  Thus, $(b_1 \cup b_2, h^1
-  \land h^2, f^1 \expmix f^2)$ contribute to $\varphi_\mu$ in
-  \eq{onestep:maxprog:guard}.  Since $(b_1 \cup b_2, h^1 \land h^2,
-  f^1 \expmix f^2)$ is enabled in $(q_1, \val{}{1}, q_2, \val{}{2}, q,
-  \val{}{})$, we have $(\val{}{1}, \val{}{2}, \val{}{}) \models h^1
-  \land h^2$ and, therefore $(\val{}{1}, \val{}{2}, \val{}{})
-  \not\models \varphi_\mu$, which contradicts \eq{guard}, thereby
-  proving that $(a \cap P_1, g^1, e^1)$ is not inhibited in
-  $\semopen{A_1(\cB)} =
-  \semopen{\mu\bigl((\IMextend{\Gamma_1}{P_1})(\cB)\bigr)}$ by the
-  maximal progress priority.
-
-  The corresponding statement for $(a \cap P_2, g^2, e^2)$ is obtained
-  symmetrically.
-\end{proof}
-
-\begin{lemma}
-  \label{lem:stepabove}
-  Consider a component $B$ and let 
-%
-  $
-  (q_1, \val{}{1})
-%
-  \goesto{a, \val[\tilde]{}{}}
-%
-  (q_2, \val{}{2})
-  $,
-%
-  be a transition in $\semopen{B}$.  For any valuation
-  $\val[\primeit]{}{1}$, such that
-  $\val{}{1} \order \val[\primeit]{}{1}$ and
-  $\valdiff{\val{}{1}}{\val[\primeit]{}{1}} \subseteq \export(a)$,
-  there exists a transition
-%
-  $
-  (q_1, \val[\primeit]{}{1})
-%
-  \goesto{a, \val[\tilde]{}{}}
-%
-  (q_2, \val{}{2})
-  $
-%
-  in $\semopen{B}$.
-\end{lemma}
-%
-\begin{proof}
-  By \eq{comp:semantics}, we have
-%
-  \begin{mathpar}
-    q_1 \goesto{a, g, e} q_2
-    \,,
-    \and
-    \val{}{1} \models g
-    \,,
-    \and
-    \val{}{2} = \val[\tilde]{}{}[e]
-    \,,
-    \and
-    \text{and}
-    \and
-    \valdiff{\val{}{1}}{\val[\tilde]{}{}} \subseteq \export(a)
-    \,.
-  \end{mathpar}
-
-  By monotonicity of guards, we deduce
-  $\val[\primeit]{}{1} \models g$.
-  For any $v \not\in \export(a)$,
-  $\val[\primeit]{}{1}(v) = \val{}{1}(v) = \val[\tilde]{}{}(v)$.
-  Hence, 
-  $\valdiff{\val[\primeit]{}{1}}{\val[\tilde]{}{}}
-  \subseteq \export(a)$.
-  By \eq{comp:semantics}, we conclude 
-%
-  $
-  (q_1, \val[\primeit]{}{1})
-%
-  \goesto{a, \val[\tilde]{}{}}
-%
-  (q_2, \val{}{2})
-  $.  
-\end{proof}
-
-\begin{proof}[Proof of \thm{combining}]
-  By \lem{onlyone}, we can assume without loss of generality that each of the two
-  architectures has only one coordinating component.  For $i =
-  1,2$, we denote $\{C_i\} = \cC_i$, $P_i = P_{C_i}
-  \cup\ \bigcup_{B \in \cB} P_B$ and $V_i = V_{C_i}
-  \cup\ \bigcup_{B \in \cB} V_B$.
-%
-  By \rem{upwards:compat}, this does not affect their upwards
-  compatibility, hence neither does this affect the applicability of
-  \lem{onestep} below.
-
-  The initiality of $\Phi_1 \land \Phi_2$, is trivial: both
-  $\Phi_1$ and $\Phi_2$ are initial, hence $s^0 \models \Phi_1
-  \land \Phi_2$.
-
-  Consider a path
-%
-  \[
-  s^0_1 s^0_2 s^0
-%
-  \goesto{a^1, \val[\tilde]{1}{}}
-%
-  s^1_1 s^1_2 s^1
-%
-  \goesto{a^2, \val[\tilde]{2}{}}
-  \cdots
-  \goesto{a^k, \val[\tilde]{k}{}}
-%
-  s^k_1 s^k_2 s^k
-  \]
-%
-  in $\semopen{(A_1 \arcomp A_2)(\cB)}$, where
-  $s^0,\dots,s^k \in \prod_{B \in \cB} S_{\semopen{B}}$ and
-  $s^0_i,\dots, s^k_i \in S_{\semopen{C_i}}$, for $i=1,2$.
-  We have to show that $s^k \models \Phi_1 \land \Phi_2$.
-
-  Assuming that $a^1 \cap P_1 \neq \emptyset$, by \lem{onestep},
-  there exists $s^{1\prime} \in \prod_{B \in \cB} S_{\semopen{B}}$,
-  such that
-%
-  \[
-  s^0_1 s^0
-%
-  \goesto{a^1 \cap P_1, \val[\doubletilde]{1}{}}
-%
-  s^1_1 s^{1\prime}
-  \]
-%
-  is a transition in $\semopen{A_1(\cB)}$ with
-  $\val[\doubletilde]{1}{}$ being the restriction of
-  $\val[\tilde]{1}{}$ to $V_1$ and
-  $s^1 \order s^{1\prime}$.
-%
-  By \lem{stepabove}, 
-  \[
-  s^1_1 s^1_2 s^{1\prime}
-%
-  \goesto{a^2, \val[\tilde]{2}{}}
-%
-  s^2_1 s^2_2 s^2
-  \]
-  is a transition in $\semopen{(A_1 \arcomp A_2)(\cB)}$ and,
-  therefore, 
-  \[
-  s^1_1 s^1_2 s^{1\prime}
-%
-  \goesto{a^2, \val[\tilde]{2}{}}
-%
-  s^2_1 s^2_2 s^2
-%
-  \goesto{a^3, \val[\tilde]{3}{}}
-  \cdots
-  \goesto{a^k, \val[\tilde]{k}{}}
-%
-  s^k_1 s^k_2 s^k
-  \]
-%  
-  is a path in $\semopen{(A_1 \arcomp A_2)(\cB)}$.
-%
-  Notice that, if the above assumption, $a^1 \cap P_1 \neq
-  \emptyset$, does not hold, then $s^0_1 = s^1_1$, $s^0 = s^1$
-  and we can take $s^{1\prime} = s^1$ in this latter path.
-
-  Repeating the entire argument $k-1$ times, starting with this
-  shorter path, we obtain a path
-%
-  \begin{equation}
-    \label{eq:path-in-1}
-    s^0_1 s^0
-    %
-    \goesto{a^1 \cap P_1, \val[\doubletilde]{1}{}}
-    %
-    s^1_1 s^{1\prime}
-    %
-    \goesto{a^2 \cap P_1, \val[\doubletilde]{2}{}}
-    %
-    s^2_1 s^{2\prime}
-    %
-    \goesto{a^3 \cap P_1, \val[\doubletilde]{3}{}}
-    \cdots
-    \goesto{a^k \cap P_1, \val[\doubletilde]{k}{}}
-    %
-    s^k_1 s^{k\prime}
-  \end{equation}
-%  
-  with $s^i \order s^{i\prime}$, for all $i \in [1,k]$.
-
-  From \eq{path-in-1}, we conclude that the state $s^k_1
-  s^{k\prime}$ is reachable in $\semopen{A_1(\cB)}$.  Since $A_1$
-  enforces $\Phi_1$ on $\cB$, this implies that $s^{k\prime}
-  \models \Phi_1$.  Since $s^k \order s^{k\prime}$, we deduce, by
-  \defn{property}, that $s^k \models \Phi_1$.
-
-  Symmetrically, $s^k \models \Phi_2$, which concludes
-  the proof.
-\end{proof}
-
-%*********************************************************************
-%*********************************************************************
-%
-%\section{pNets additional definitions}
-%\label{secn:pNets:additional}
-%
-%\begin{definition}[Sorts, Holes, Leaves of pNets]
-%  \begin{itemize}
-%  \item  \noteSB{I think this can be lightened up a bit, since the definitions are all 
-%  straightforward, whereas the notation is complex.  Maybe reformulate in words and move 
-%  the formal definitions in the appendix?}
-% The sort of a pNet is its signature, i.e. the set of actions it can
-%perform. \noteSB{Is there any chance that, by writing assignments explicitly ($x := e$), 
-%we could eliminate the need to distinguish the input variables at all? That would 
-%simplify things.}\hl{In the definition of sorts, we do not need to distinguish
-%input variables} (that specify the dataflow within LTSs), so for
-%computing LTS sorts, we use a substitution operator\footnote{$\subst{y_k\gets x_k}^{k\in 
-%K}$ is the parallel substitution 
-%operation.} to remove the
-%\emph{input marker} of variables\footnote{$\overline{S}$ denotes a set of $S$.}. Formally:
-%\[
-%\begin{array}{l}
-%\Sortop(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{x \gets ?x| 
-%x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~g,~(x_j\!:= {e}_j)^{j\in
-%    J}\rangle} s'\in \to \} \\
-%\Sortop(\mylangle \overline{\pNet}\!, %\pNet_i^{i\in I}, \Sort_j^{j\in J}
-%\overline{\pNet}\!,
-%\overline{\symb{SV}}\myrangle)
-%=\{\alpha' |\, \overline{\alpha}%\alpha_j^{j\in J_k}
-%\to\alpha'\in\set{\symb{SV}}\}
-%\end{array}
-%\]
-%
-%\item
-%The set of holes of a pNet is defined inductively; the sets of holes
-%in a pNet node and its subnets are all disjoint:
-%  \[\begin{array}{l}
-%\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset \\
-%\Holes(\mylangle \pNet_i^{i\in I}\!,\Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) 
-%=J\uplus{\displaystyle \bigcup_{i\in 
-%I}\Holes(\pNet_i)}\\
-%\forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
-%\forall i_1,i_2\in I.\,i_1\neq i_2\Rightarrow  
-%\Holes(\pNet_{i_1})\cap\Holes(\pNet_{i_2})=\emptyset
-%\end{array}\]
-%\item
-%The set of leaves of a pNet is the set of all pLTSs occurring in the structure, defined 
-%inductively as:
-%\[\begin{array}{l}
-%\Leaves(\mylangle S,s_0, \to\myrangle) \!=\!\emptyset\\%\{\mylangle S,s_0, \to\myrangle\}\\
-%\Leaves(\mylangle \pNet_i^{i\in I}\!,%Sort_j^{j\in J}
-%\overline{\Sort}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \biguplus_{i\in 
-%I}\Leaves(\pNet_i)\uplus\{i\mapsto \pNet_i|\pNet_i\pNet_i \text{ is a }\pLTS\}}
-%\end{array}\]
-%\end{itemize}
-%\end{definition}
-
-%*********************************************************************
-%*********************************************************************
-
 \section{Algebraic representations of the interaction model}
@@
 
-In this section condensed from
-\cite[Section~4]{BarBliu15-offer-scico}, we briefly recall the syntax
+This section presents some material that has already been published in earlier work but is essential for understanding the encoding in \secn{encoding}.
+It is condensed from
+\cite[Section~4]{BarBliu15-offer-scico} and recalls briefly the syntax
 and semantics of the algebras used to represent BIP interaction models
-\emph{disregarding variables and data transfer}.  All the algebras are
+\emph{disregarding variables and data transfer}.
+
+All the algebras are
 parameterised by a set $P$ of all the ports in a given system.  The
@@
 
-\begin{figure}
+\begin{figure}[t]
   \centering
@@
 
-\section{Additional material for the theory of architectures}
+%*********************************************************************
+%*********************************************************************
+
+\section{Additional definitions for the theory of architectures}
 \label{secn:arch:appendix}
@@
 
+%****************************************************************
+%****************************************************************
+
+\section{Proofs}
+\label{secn:proofs}
+
+\begin{lemma}
+  \label{lem:onlyone}
+  Let $A = \tuple{\cC, V_A, P_A, \export[A], \Gamma}$ be an architecture and denote
+  by $\Gamma_\cC \bydef{=}
+%
+  \setdef{
+    (a \cap P_\cC, \true, \noop)
+  }{
+    (a, g, e) \in \Gamma
+  }$, with $P_\cC = \bigcup_{C \in \cC} P_C$,
+%  
+  the projection of $\Gamma$ onto the coordinating components of
+  $A$.  Consider the architecture $A' = \tuple{\{C'\}, V_A, P_A, \export[A],
+  \Gamma}$, where $C' = \Gamma_\cC(\cC)$.  For any set of
+  components $\cB$, satisfying the conditions of
+  \defn{arch:application}, we have
+  $\semopen{A(\cB)} = \semopen{A'(\cB)}$.
+\end{lemma}
+%
+\begin{proof}
+  First of all, notice that, by \defn{im:sem},
+  $V_{C'} = \bigcup_{C \in \cC} V_C$ and $P_{C'} = P_\cC = \bigcup_{C \in \cC} P_C$.
+  The conditions of \defn{arch} are satisfied and $A'$ is indeed
+  an architecture.  Furthermore, $\cB$ satisfies the conditions
+  of \defn{arch:application} \wrt $A'$.  Hence, the component
+  $A'(\cB)$ is well defined.
+
+  Clearly the state spaces and initial states %% and interfaces
+  of both LTSs $\semopen{A(\cB)}$ and $\semopen{A'(\cB)}$
+  coincide.  Thus, we only have to prove that so do the
+  transition relations.  Let us assume that
+  $\cC = C_i^{i \in I}$ and $\cB = B_j^{j \in J}$.
+  We will use $q_i, q_i'$ to denote the states of
+  $C_i$ and $q_j, q_j'$ to denote the states of $B_j$,
+  and similarly for the valuations of variables.
+
+  By \defn{comp:semantics},
+%
+  \begin{equation}
+    \label{eq:lem1:trans:sem}
+    (q_i, \val{}{i})^{i \in I} (q_j, \val{}{j})^{j \in J}
+    \goesto{a, \val[\tilde]{}{}}
+    (q_i', \val{\prime}{i})^{i \in I}
+    (q_j', \val{\prime}{j})^{j \in J}
+  \end{equation}
+%  
+  is a transition in $\semopen{A(\cB)}$ (\resp
+  $\semopen{A'(\cB)}$) iff
+%
+  \begin{equation}
+    \label{eq:lem1:trans}
+    q_i^{i \in I} q_j^{j \in J}
+    \goesto{a, g', e'}
+    (q_i')^{i \in I} (q_j')^{j \in J}
+    \,,
+  \end{equation}
+%
+  is a transition in $A(\cB)$ (\resp $A'(\cB)$) and
+%
+  \begin{mathpar}
+    \val{i \in I}{i} \val{j \in J}{j}
+    \models g'
+    \,,
+    \and
+    (\val{\prime}{i})^{i \in I} (\val{\prime}{j})^{j \in J}
+    = \val[\tilde]{}{}[e']
+    \,,
+    \and
+    \valdiff{\val{i \in I}{i} \val{j \in J}{j}}{
+      \val[\tilde]{}{}} \subseteq \export(a)       
+  \end{mathpar}
+%
+  (with $\export$ defined as in \defn{arch:application}).
+
+  By \defn{im:sem} and \defn{priority:sem}, \eq{lem1:trans} is a transition in $A(\cB)$
+  iff $a \neq \emptyset$, $(a, g, e) \in \IMextend{\Gamma}{P}$,
+  where $P = \bigcup_{B \in \cB \cup \cC} P_B$, and
+  %
+  \begin{enumerate}
+  \item\label{ab:start} for $i \in I$,\\
+    $a \cap P_{C_i} \neq \emptyset$ and
+    $q_i \goesto{a \cap P_{C_i},\, g_{C_i},\, e_{C_i}} q_i'$
+    is a transition in $C_i$, or\\
+    $a \cap P_{C_i} = \emptyset$ and $q_i = q_i'$
+    (for covenience, we put $g_{C_i} = \true$ and $e_{C_i} = \noop$ in item~\ref{aux1} below);
+  \item for $j \in J$,\\
+    $a \cap P_{B_j} \neq \emptyset$ and
+    $q_j \goesto{a \cap P_{B_j},\, g_{B_j},\, e_{B_j}} q_j'$
+    is a transition in $B_j$, or\\
+    $a \cap P_{B_j} = \emptyset$ and $q_j = q_j'$
+    (for covenience, we put $g_{B_j} = \true$ and $e_{B_j} = \noop$ in item~\ref{aux1} below);
+  \item\label{ab:end}\label{aux1} $g' = g \land \bigwedge_{i \in I} g_{C_i} \land
+    \bigwedge_{j \in J} g_{B_j} \land \varphi_\mu$ and
+    $e' = e; e_{C_i}^{i \in I}, e_{B_j}^{j \in J}$, where    
+%
+    \begin{equation}
+      \label{eq:only1:maxprog:guard}
+      \varphi_\mu = \bigwedge_{
+        \begin{array}{c}
+          q_i^{i \in I} q_j^{j \in J} \goesto{b, h, f} \text{ in }
+          (\IMextend{\Gamma}{P})(\cC \cup \cB)
+          \\
+          a \varsubsetneq b
+        \end{array}
+      } \lnot h
+      \,.
+    \end{equation}
+%
+  \breakenumistart
+
+  Similarly, \eq{lem1:trans} is a transition in
+  $A'(\cB)$ iff $a \neq \emptyset$,
+  $(a, g, e) \in \IMextend{\Gamma}{P}$ and
+%
+  \breakenumiend
+% 
+  \item \label{a1b:start} \label{only1:coord}
+    $a \cap P_{C'} \neq \emptyset$ and 
+    $(q_i)^{i \in I} \goesto{a \cap P_{C'}, g_{C'}, e_{C'}} (q_i')^{i \in I}$
+    is a transition in $C'$, or\\
+    $a \cap P_{C'} = \emptyset$ and $q_i = q_i'$,
+    for all $i \in [1,m]$
+    (for covenience, we put $g_{C'} = \true$ and $e_{C'} = \noop$ in
+    item~\ref{aux2} below);
+  \item for $j \in J$,\\
+    $a \cap P_{B_j} \neq \emptyset$ and
+    $q_j \goesto{a \cap P_{B_j}, g_{B_j}, e_{B_j}} q_j'$
+    is a transition in $B_j$, or\\
+    $a \cap P_{B_j} = \emptyset$ and $q_j = q_j'$
+    (for covenience, we put $g_{B_j} = \true$ and $e_{B_j} = \noop$ in
+    item~\ref{aux2} below);
+  \item\label{aux2} $g' = g \land g_{C'} \land
+    \bigwedge_{j \in J} g_{B_j} \land \varphi_\mu'$ and
+    $e' = e; e_{C'}, e_{B_j}^{j \in J}$ (with $\varphi_\mu'$ defined as
+    in \eq{only1:maxprog:guard}, but substituting $\{C'\}$ instead of $\cC$).
+%
+  \breakenumistart
+  Notice that, for any $i \in I$, since
+  $P_{C_i} \subseteq P_{C'}$, we have
+  $a \cap P_{C_i} = (a \cap P_{C'}) \cap P_{C_i}$.
+  Thus, if $a \cap P_{C'} \neq \emptyset$, 
+  the transition in condition~\ref{only1:coord} above is
+  present in $C'$ iff
+  $(a \cap P_{C'}, \true, \noop) \in \Gamma_\cC$ and
+  \breakenumiend
+% 
+  \item for $i \in I$,\\
+    $a \cap P_{C_i} \neq \emptyset$ and
+    $q_i \goesto{a \cap P_{C_i}, g_{C_i}, e_{C_i}} q_i'$
+    is a transition in $C_i$, or\\
+    $a \cap P_{C_i} = \emptyset$ and $q_i = q_i'$,
+    (for covenience, we put $g_{C_i} = \true$ and $e_{C_i} = \noop$ in
+    item~\ref{aux3} below);
+  \item \label{a1b:end} \label{aux3} $g_{C'} = \bigwedge_{i \in I} g_{C_i}$ and
+    $e_{C'} = e_{C_i}^{i \in I}$.
+  \end{enumerate}
+
+  Consider $(a,g,e) \in \IMextend{\Gamma}{P}$.  By
+  \defn{arch:application}, this is equivalent to
+  $(a \cap P_A, g, e) \in \Gamma$.
+  Since $P_{C'} = P_\cC \subseteq P_A$, we have
+  $a \cap P_{C'} = a \cap P_\cC = (a \cap P_A) \cap P_\cC$.
+  Hence, by the definition of $\Gamma_\cC$ in the lemma statement,
+  this is also equivalent to
+  $(a \cap P_{C'}, \true, \noop) \in \Gamma_\cC$.
+
+  Thus, conditions \ref{ab:start}\ndash\ref{ab:end} are satisfied iff
+  so are conditions \ref{a1b:start}\ndash\ref{a1b:end} (to see that
+  $\varphi_\mu$ is satisfied iff so is $\varphi_\mu'$, one has to
+  consider the same two sets of conditions, but this time without the
+  additional conjuncts $\varphi_\mu$ and $\varphi_\mu'$ in
+  items~\ref{aux1} and \ref{aux2}, since no priority model is applied
+  to obtain $C'$).  This proves that the transition relations of
+  $\semopen{A(\cB)}$ and $\semopen{A'(\cB)}$ coincide and, therefore,
+  $\semopen{A(\cB)} = \semopen{A'(\cB)}$.
+\end{proof}
+
+\begin{note}
+  \label{rem:upwards:compat}
+  Notice that, since, in the statement of \lem{onlyone}, 
+  %
+  \begin{enumerate}
+  \item the interaction models are the same for both $A$ and $A'$, and
+  \item $P_{C'} = P_\cC$,
+  \end{enumerate}
+  %
+  substituting $A'$ for $A$ preserves upwards compatibility, \ie for any
+  architecture $A''$, holds the following statement: $A$ and $A''$ are
+  upwards compatible if and only if so are $A'$ and $A''$.
+\end{note}
+
+\begin{lemma}
+  \label{lem:onestep}
+  Let $\cB$ be a set of components; let $A_i = \tuple{\{C_i\}, V_{A_i},
+  P_{A_i}, \export[A_i], \Gamma_i}$, for $i = 1,2$, be two upwards compatible architectures
+  with one coordinator each, applicable to $\cB$.  Denote
+  $P_i = P_{C_i} \cup \bigcup_{B \in \cB} P_B$.
+  Finally, let
+%
+  $
+  s_1 s_2 s
+%
+  \goesto{a, \tilde{\val{}{}}}
+%
+  s_1' s_2' s'
+  $,
+%
+  be a transition in $\semopen{(A_1 \arcomp A_2)(\cB)}$, with
+  $a \neq \emptyset$, 
+  $s, s' \in \prod_{B \in \cB} S_{\semopen{B}}$
+  and
+  $s_i, s_i' \in S_{\semopen{C_i}}$ ($i=1,2$).
+%
+  Then, for $i=1,2$, either $a \cap P_i = \emptyset$ and $s_i s=
+  s_i' s'$, or there exists a transition
+%
+  $
+  s_i s
+%
+  \goesto{a \cap P_i, \val[\doubletilde]{}{}}
+%
+  s_i' s''
+  $ 
+%
+  in $\semopen{A_i(\cB)}$, with
+  $\val[\doubletilde]{}{}$ being the restriction of
+  $\val[\tilde]{}{}$ to
+  $V_i = V_{C_i} \cup \bigcup_{B \in \cB} V_B$ and
+  $s' \order s''$.
+\end{lemma}
+%
+\begin{proof}
+  By \defn{comp:semantics}, every semantic state consists of a
+  component state and a valuation of component variables.  Thus,
+  we can expand $s_1 s_2 s \goesto{a, \tilde{\val{}{}}} s_1' s_2' s'$
+  as
+%
+  \[
+  (q_1, \val{}{1}, q_2, \val{}{2}, q, \val{}{})
+%
+  \goesto{a, \tilde{\val{}{}}}
+%
+  (q_1', \val[\primeit]{}{1}, q_2', \val[\primeit]{}{1}, q', \val[\primeit]{}{})
+  \,.
+  \]
+%
+  By \defn{im:sem} and \defn{priority:sem}, this implies
+  that
+  $(q_1, q_2, q) \goesto {a, g', e'} (q_1', q_2', q')$
+  is a transition in $(A_1 \arcomp A_2)(\cB)$, with
+%
+  $g' = g \land g_1 \land g_2 \land g_\cB \land \varphi_\mu$
+  and
+  $e' = e; (e_1, e_2, e_\cB)$,
+  where $(a, g, e) \in \Gamma$ (see \eq{arch:composition} for the
+  definition of $\Gamma$);
+%  
+  $g_1$, $g_2$ and $e_1$, $e_2$ are, respectively, the guards and
+  update expressions of the underlying transitions in the coordinating
+  components $C_1$ and $C_2$;
+%    
+  \begin{mathpar}
+    g_\cB = \bigwedge_{B \in \supp{a} \cap \cB} g_B
+    \,,
+    \and
+    e_\cB = e_B^{B \in \supp{a} \cap \cB}
+    \,,
+  \end{mathpar}
+%
+  are the compositions of, respectively, the guards and update
+  expressions of the operand components;
+%    
+  \begin{equation}
+    \label{eq:onestep:maxprog:guard}
+    \varphi_\mu = \bigwedge_{
+      \begin{array}{c}
+        (q_1, q_2, q) \goesto{b, h', f'} \text{ in }
+        \bigl(\IMextend{\Gamma}{(P_1 \cup P_2)}\bigr)
+        \bigl(\{C_1, C_2\} \cup \cB\bigr)
+        \\
+        a \varsubsetneq b
+      \end{array}
+    } \lnot h'
+  \end{equation}
+%
+  is the conjunct encoding the maximal progress priority in
+  \defn{priority:sem}.  As above for $g'$, for each $(b, h', f')$ in
+  \eq{onestep:maxprog:guard}, $h'$ can be decomposed as $h' = h \land
+  h_1 \land h_2 \land h_\cB$ (without the maximal progress conjunct,
+  since no priority is applied in $\bigl(\IMextend{\Gamma}{(P_1 \cup
+    P_2)}\bigr)\bigl(\{C_1, C_2\} \cup \cB\bigr)$).
+
+  By \eq{comp:semantics}, we also have
+%
+  \begin{align}
+    \label{eq:guard}
+    (\val{}{1}, \val{}{2}, \val{}{}) &\models g'
+    \,,
+    \\
+    \label{eq:substitution}
+    (\val[\primeit]{}{1}, \val[\primeit]{}{2}, \val[\primeit]{}{})
+    &= \val[\tilde]{}{}[e']
+    \,,
+    \\
+    \label{eq:transient}
+    \valdiff{(\val{}{1}, \val{}{2}, \val{}{})}{\val[\tilde]{}{}}
+    &\subseteq \export(a)
+    \,.
+  \end{align}
+%
+  If $a \cap P_1 = \emptyset$, then $\supp{a} = \{C_2\}$ and, by
+  \eq{transient} and \defn{im:sem}, $s_1 = s_1'$ and $s = s'$
+  (recall, \defn{im}, that, for $(a,g,e) \in \Gamma$, we have $e
+  \in \exprs{V_a}$).  Hereafter, assume $a \cap P_1 \neq
+  \emptyset$.
+
+  By \eq{arch:composition}, for $i=1,2$, there exist $(a \cap P_{A_i},
+  g^i, e^i) \in \Gamma_i$, such that $g = g^1 \land g^2$ and $e = e^1
+  \land e^2$.
+  %% Similarly, for each $(b, h', f')$ in \eq{onestep:maxprog:guard},
+  %% there exist $(b \cap P_{A_i}, h^i, f^i) \in \Gamma_i$, such that
+  %% $h = h^1 \land h^2$ and $f = f^1 \land f^2$.
+%
+  We want to show that the interaction $(a \cap P_1, g^1, e^1)$ is
+  enabled in the state $(q_1, \val{}{1}, q, \val{}{})$ of
+  $\semopen{A_1(\cB)}$.  To this end, we proceed in two steps:
+%
+  \begin{enumerate}
+  \item \label{onestep:proof:im} We show that $(a \cap P_1, g^1,
+    e^1)$ is enabled in the state $(q_1, \val{}{i}, q, \val{}{})$ of
+    $\semopen{(\IMextend{\Gamma_1}{P_1})(\cB)}$.
+  \item \label{onestep:proof:maxp} We show that $(a \cap P_1, g^1,
+    e^1)$ is not inhibited in $\semopen{A_1(\cB)} =
+    \semopen{\mu\bigl((\IMextend{\Gamma_1}{P_1})(\cB)\bigr)}$ by the
+    maximal progress priority.
+  \end{enumerate}
+
+  \paragraph*{Step \ref{onestep:proof:im}}
+  %% Denoting $P_\cB = \bigcup_{B \in \supp{a} \cap \cB} P_B$, 
+  By \defn{im:sem}, we have
+%
+  \begin{mathpar}
+    q_1 \goesto{a \cap P_{C_1}, g_1, e_1} q_1'
+    \and
+    \text{and}
+    \and
+    q_B \goesto{a \cap P_B, g_B, e_B} q_B',
+    \text{ for each }
+    B \in \cB
+    \,.
+  \end{mathpar}
+
+  By \eq{guard}, we have
+  $(\val{}{1}, \val{}{}) \models g^1 \land g_1 \land g_\cB$.
+
+  Denoting \todoSB{One tilde is enough}$\val[\doubletilde]{}{1}$ the restriction of
+%
+  $\val[\tilde]{}{}$ to
+  $V_1 = V_{C_1} \cup \bigcup_{B \in \cB} V_B$,
+%
+  we have, by \eq{substitution} and the monotonicity of
+  expressions,
+%
+  $(\val[\primeit]{}{1}, \val[\primeit]{}{}) \order
+  \val[\doubletilde]{}{1}[e^1; (e_1, e_b)]$.  \todoSB{Remove this}\hl{Notice that all
+  variables affected by both $e^1$ and $e^2$ must necessarily
+  belong to $\bigcup_{B \in \cB} V_B$.}  Hence,
+%
+  $\val[\doubletilde]{}{1}[e^1; (e_1, e_b)] =
+  (\val[\primeit]{}{1}, \val[\secondit]{}{})$ with 
+  $\val[\primeit]{}{} \order \val[\secondit]{}{}$.
+
+  By \defn{comp:semantics} and \defn{im:sem}, we have
+  $
+  (q_1, \val{}{1}, q, \val{}{})
+  \goesto{a \cap P_1, \val[\doubletilde]{}{1}}
+  (q_1', \val[\primeit]{}{1}, q, \val[\secondit]{}{})
+  $ in $\semopen{(\IMextend{\Gamma_1}{P_1})(\cB)}$.
+
+  Symmetrically, we have 
+  $
+  (q_2, \val{}{2}, q, \val{}{})
+  \goesto{a \cap P_2, \val[\doubletilde]{}{2}}
+  (q_2', \val[\primeit]{}{2}, q, \val[\secondit]{}{})
+  $ in $\semopen{(\IMextend{\Gamma_2}{P_2})(\cB)}$.
+
+  \paragraph*{Step \ref{onestep:proof:maxp}}
+  Suppose that $a \cap P_1 \varsubsetneq b_1$, for some interaction
+  $(b_1, h^1, f^1) \in \IMextend{\Gamma_1}{P_1}$ enabled in $(q_1,
+  \val{}{1}, q, \val{}{})$.  Then, by upwards compatibility of $A_1$
+  and $A_2$, there exists $(b_2, h^2, f^2) \in
+  \IMextend{\Gamma_2}{P_2}$, enabled in $(q_2, \val{}{2}, q,
+  \val{}{})$, such that $a \cap P_2 \subseteq b_2$ and $b_2 \cap P_1 =
+  b_1 \cap P_2$.  By \defn{arch:application}, we have $(b_1 \cap P_{A_1},
+  h^1, e^1) \in \Gamma^1$.  Furthermore,
+%
+  \begin{multline*}
+    ((b_1 \cap P_{A_1}) \cup (b_2 \cap P_{A_2}))  \cap P_{A_1} =
+    (b_1 \cap P_{A_1}) \cup (b_2 \cap P_{A_1} \cap P_{A_2}) =\\
+    (b_1 \cap P_{A_1}) \cup ((b_2 \cap P_1) \cap P_{A_1} \cap P_{A_2}) =  
+    (b_1 \cap P_{A_1}) \cup ((b_1 \cap P_2) \cap P_{A_1} \cap P_{A_2}) =\\
+    (b_1 \cup (b_1 \cap P_2 \cap P_{A_2})) \cap P_{A_1} =
+    b_1 \cap P_{A_1} 
+  \end{multline*}
+%
+  Symmetrically, $(b_2 \cap P_{A_2}, h^2, e^2) \in \Gamma^2$ and
+  $((b_1 \cap P_{A_1}) \cup (b_2 \cap P_{A_2})) \cap P_{A_2} = b_2
+  \cap P_{A_2}$.  By \eq{arch:composition}, we then have $((b_1 \cap
+  P_{A_1}) \cup (b_2 \cap P_{A_2}), h^1 \land h^2, f^1 \expmix f^2)
+  \in \Gamma$ and, by \defn{arch:application}, $(b_1 \cup b_2, h^1 \land
+  h^2, f^1 \expmix f^2) \in \IMextend{\Gamma}{(P_1 \cup P_2)}$.
+%
+  Since both $(b_i, h^i, f^i) \in \IMextend{\Gamma_i}{P_i}$ are
+  enabled in the respective states $(q_i, \val{}{i}, q, \val{}{})$, we
+  conclude that $(b_1 \cup b_2, h^1 \land h^2, f^1 \expmix f^2)$ is
+  enabled in $(q_1, \val{}{1}, q_2, \val{}{2}, q, \val{}{})$.
+
+  Since $a \cap P_1 \varsubsetneq b_1$ and $a \cap P_2 \subseteq b_2$,
+  we have $a \varsubsetneq b_1 \cup b_2$.  Thus, $(b_1 \cup b_2, h^1
+  \land h^2, f^1 \expmix f^2)$ contribute to $\varphi_\mu$ in
+  \eq{onestep:maxprog:guard}.  Since $(b_1 \cup b_2, h^1 \land h^2,
+  f^1 \expmix f^2)$ is enabled in $(q_1, \val{}{1}, q_2, \val{}{2}, q,
+  \val{}{})$, we have $(\val{}{1}, \val{}{2}, \val{}{}) \models h^1
+  \land h^2$ and, therefore $(\val{}{1}, \val{}{2}, \val{}{})
+  \not\models \varphi_\mu$, which contradicts \eq{guard}, thereby
+  proving that $(a \cap P_1, g^1, e^1)$ is not inhibited in
+  $\semopen{A_1(\cB)} =
+  \semopen{\mu\bigl((\IMextend{\Gamma_1}{P_1})(\cB)\bigr)}$ by the
+  maximal progress priority.
+
+  The corresponding statement for $(a \cap P_2, g^2, e^2)$ is obtained
+  symmetrically.
+\end{proof}
+
+\begin{lemma}
+  \label{lem:stepabove}
+  Consider a component $B$ and let 
+%
+  $
+  (q_1, \val{}{1})
+%
+  \goesto{a, \val[\tilde]{}{}}
+%
+  (q_2, \val{}{2})
+  $,
+%
+  be a transition in $\semopen{B}$.  For any valuation
+  $\val[\primeit]{}{1}$, such that
+  $\val{}{1} \order \val[\primeit]{}{1}$ and
+  $\valdiff{\val{}{1}}{\val[\primeit]{}{1}} \subseteq \export(a)$,
+  there exists a transition
+%
+  $
+  (q_1, \val[\primeit]{}{1})
+%
+  \goesto{a, \val[\tilde]{}{}}
+%
+  (q_2, \val{}{2})
+  $
+%
+  in $\semopen{B}$.
+\end{lemma}
+%
+\begin{proof}
+  By \eq{comp:semantics}, we have
+%
+  \begin{mathpar}
+    q_1 \goesto{a, g, e} q_2
+    \,,
+    \and
+    \val{}{1} \models g
+    \,,
+    \and
+    \val{}{2} = \val[\tilde]{}{}[e]
+    \,,
+    \and
+    \text{and}
+    \and
+    \valdiff{\val{}{1}}{\val[\tilde]{}{}} \subseteq \export(a)
+    \,.
+  \end{mathpar}
+
+  By monotonicity of guards, we deduce
+  $\val[\primeit]{}{1} \models g$.
+  For any $v \not\in \export(a)$,
+  $\val[\primeit]{}{1}(v) = \val{}{1}(v) = \val[\tilde]{}{}(v)$.
+  Hence, 
+  $\valdiff{\val[\primeit]{}{1}}{\val[\tilde]{}{}}
+  \subseteq \export(a)$.
+  By \eq{comp:semantics}, we conclude 
+%
+  $
+  (q_1, \val[\primeit]{}{1})
+%
+  \goesto{a, \val[\tilde]{}{}}
+%
+  (q_2, \val{}{2})
+  $.  
+\end{proof}
+
+\begin{proof}[Proof of \thm{combining}]
+  By \lem{onlyone}, we can assume without loss of generality that each of the two
+  architectures has only one coordinating component.  For $i =
+  1,2$, we denote $\{C_i\} = \cC_i$, $P_i = P_{C_i}
+  \cup\ \bigcup_{B \in \cB} P_B$ and $V_i = V_{C_i}
+  \cup\ \bigcup_{B \in \cB} V_B$.
+%
+  By \rem{upwards:compat}, this does not affect their upwards
+  compatibility, hence neither does this affect the applicability of
+  \lem{onestep} below.
+
+  The initiality of $\Phi_1 \land \Phi_2$, is trivial: both
+  $\Phi_1$ and $\Phi_2$ are initial, hence $s^0 \models \Phi_1
+  \land \Phi_2$.
+
+  Consider a path
+%
+  \[
+  s^0_1 s^0_2 s^0
+%
+  \goesto{a^1, \val[\tilde]{1}{}}
+%
+  s^1_1 s^1_2 s^1
+%
+  \goesto{a^2, \val[\tilde]{2}{}}
+  \cdots
+  \goesto{a^k, \val[\tilde]{k}{}}
+%
+  s^k_1 s^k_2 s^k
+  \]
+%
+  in $\semopen{(A_1 \arcomp A_2)(\cB)}$, where
+  $s^0,\dots,s^k \in \prod_{B \in \cB} S_{\semopen{B}}$ and
+  $s^0_i,\dots, s^k_i \in S_{\semopen{C_i}}$, for $i=1,2$.
+  We have to show that $s^k \models \Phi_1 \land \Phi_2$.
+
+  Assuming that $a^1 \cap P_1 \neq \emptyset$, by \lem{onestep},
+  there exists $s^{1\prime} \in \prod_{B \in \cB} S_{\semopen{B}}$,
+  such that
+%
+  \[
+  s^0_1 s^0
+%
+  \goesto{a^1 \cap P_1, \val[\doubletilde]{1}{}}
+%
+  s^1_1 s^{1\prime}
+  \]
+%
+  is a transition in $\semopen{A_1(\cB)}$ with
+  $\val[\doubletilde]{1}{}$ being the restriction of
+  $\val[\tilde]{1}{}$ to $V_1$ and
+  $s^1 \order s^{1\prime}$.
+%
+  By \lem{stepabove}, 
+  \[
+  s^1_1 s^1_2 s^{1\prime}
+%
+  \goesto{a^2, \val[\tilde]{2}{}}
+%
+  s^2_1 s^2_2 s^2
+  \]
+  is a transition in $\semopen{(A_1 \arcomp A_2)(\cB)}$ and,
+  therefore, 
+  \[
+  s^1_1 s^1_2 s^{1\prime}
+%
+  \goesto{a^2, \val[\tilde]{2}{}}
+%
+  s^2_1 s^2_2 s^2
+%
+  \goesto{a^3, \val[\tilde]{3}{}}
+  \cdots
+  \goesto{a^k, \val[\tilde]{k}{}}
+%
+  s^k_1 s^k_2 s^k
+  \]
+%  
+  is a path in $\semopen{(A_1 \arcomp A_2)(\cB)}$.
+%
+  Notice that, if the above assumption, $a^1 \cap P_1 \neq
+  \emptyset$, does not hold, then $s^0_1 = s^1_1$, $s^0 = s^1$
+  and we can take $s^{1\prime} = s^1$ in this latter path.
+
+  Repeating the entire argument $k-1$ times, starting with this
+  shorter path, we obtain a path
+%
+  \begin{equation}
+    \label{eq:path-in-1}
+    s^0_1 s^0
+    %
+    \goesto{a^1 \cap P_1, \val[\doubletilde]{1}{}}
+    %
+    s^1_1 s^{1\prime}
+    %
+    \goesto{a^2 \cap P_1, \val[\doubletilde]{2}{}}
+    %
+    s^2_1 s^{2\prime}
+    %
+    \goesto{a^3 \cap P_1, \val[\doubletilde]{3}{}}
+    \cdots
+    \goesto{a^k \cap P_1, \val[\doubletilde]{k}{}}
+    %
+    s^k_1 s^{k\prime}
+  \end{equation}
+%  
+  with $s^i \order s^{i\prime}$, for all $i \in [1,k]$.
+
+  From \eq{path-in-1}, we conclude that the state $s^k_1
+  s^{k\prime}$ is reachable in $\semopen{A_1(\cB)}$.  Since $A_1$
+  enforces $\Phi_1$ on $\cB$, this implies that $s^{k\prime}
+  \models \Phi_1$.  Since $s^k \order s^{k\prime}$, we deduce, by
+  \defn{property}, that $s^k \models \Phi_1$.
+
+  Symmetrically, $s^k \models \Phi_2$, which concludes
+  the proof.
+\end{proof}
+
+%*********************************************************************
+%*********************************************************************
+%
+%%\section{pNets additional definitions}
+%\label{secn:pNets:additional}
+%
+%\begin{definition}[Sorts, Holes, Leaves of pNets]
+%  \begin{itemize}
+%  \item  \noteSB{I think this can be lightened up a bit, since the definitions are all 
+%  straightforward, whereas the notation is complex.  Maybe reformulate in words and move 
+%  the formal definitions in the appendix?}
+% The sort of a pNet is its signature, i.e. the set of actions it can
+%perform. \noteSB{Is there any chance that, by writing assignments explicitly ($x := e$), 
+%we could eliminate the need to distinguish the input variables at all? That would 
+%simplify things.}\hl{In the definition of sorts, we do not need to distinguish
+%input variables} (that specify the dataflow within LTSs), so for
+%computing LTS sorts, we use a substitution operator\footnote{$\subst{y_k\gets x_k}^{k\in 
+%K}$ is the parallel substitution 
+%operation.} to remove the
+%\emph{input marker} of variables\footnote{$\overline{S}$ denotes a set of $S$.}. Formally:
+%\[
+%\begin{array}{l}
+%\Sortop(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{x \gets ?x| 
+%x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~g,~(x_j\!:= {e}_j)^{j\in
+%    J}\rangle} s'\in \to \} \\
+%\Sortop(\mylangle \overline{\pNet}\!, %\pNet_i^{i\in I}, \Sort_j^{j\in J}
+%\overline{\pNet}\!,
+%\overline{\symb{SV}}\myrangle)
+%=\{\alpha' |\, \overline{\alpha}%\alpha_j^{j\in J_k}
+%\to\alpha'\in\set{\symb{SV}}\}
+%\end{array}
+%\]
+%
+%\item
+%The set of holes of a pNet is defined inductively; the sets of holes
+%in a pNet node and its subnets are all disjoint:
+%  \[\begin{array}{l}
+%\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset \\
+%\Holes(\mylangle \pNet_i^{i\in I}\!,\Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) 
+%=J\uplus{\displaystyle \bigcup_{i\in 
+%I}\Holes(\pNet_i)}\\
+%\forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
+%\forall i_1,i_2\in I.\,i_1\neq i_2\Rightarrow  
+%\Holes(\pNet_{i_1})\cap\Holes(\pNet_{i_2})=\emptyset
+%\end{array}\]
+%\item
+%The set of leaves of a pNet is the set of all pLTSs occurring in the structure, defined 
+%inductively as:
+%\[\begin{array}{l}
+%\Leaves(\mylangle S,s_0, \to\myrangle) \!=\!\emptyset\\%\{\mylangle S,s_0, \to\myrangle\}\\
+%\Leaves(\mylangle \pNet_i^{i\in I}\!,%Sort_j^{j\in J}
+%\overline{\Sort}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \biguplus_{i\in 
+%I}\Leaves(\pNet_i)\uplus\{i\mapsto \pNet_i|\pNet_i\pNet_i \text{ is a }\pLTS\}}
+%\end{array}\]
+%\end{itemize}
+%\end{definition}
+
+%*********************************************************************
+%*********************************************************************
+
 \section{Additional material for the case study}

### 2019-02-19 2018-Arch-pNets/arch-pNets.tex
arch-pNets paper: Some improvements in - the discussion of alphas (fresh names of the SVs in the encoding) - verification discussion at end of Sect 4 NB: Added the Boolean variables to the alphas in the encoding.

@@
 \newcommand{\addspace}[1]{#1 }
-\newcommand{\nopri}[1][]{\ensuremath{\mathit{pNet}%
+\newcommand{\nopri}[1][]{\ensuremath{\mathit{enc}%
     \ifx#1\relax\else(#1)\fi}}
-\newcommand{\maxprog}[1][]{\ensuremath{\mathit{pNet}_\mu%
+\newcommand{\maxprog}[1][]{\ensuremath{\mathit{enc}_\mu%
     \ifx#1\relax\else(#1)\fi}}
@@
 \begin{example}[An open-transition]
-  \label{Example:TimerOT3}
+  \label{ex:TimerOT3}
 We now briefly illustrate an open transition:
@@
 ports {\PortFail} and {\NameCtrl.\PortFail}.
-The guard $b_1 \Rightarrow b_0$ encodes the causal
-relation between ports {\NameCtrl.\PortFail} and {\PortFail}.  Notice
-that, in our encoding, all three ports are present in the
+The guard $b1 \Rightarrow b0$ encodes the causal
+relation between these ports.  Notice
+that %% , in our encoding,
+all three ports are present in the
 synchronisation vector.  \Fig{FailureTimer:pNet} shows
@@
 SV4, synchronising the {\init} transitions of the two pLTSs.
-
-\addSB{In the general encoding, the global actions of the
-  synchronisation vectors should be fresh action names.  However, for
-  the properties considered in our case study, we only need to exhibit
-  the actions of the holes.  Furthermore, each synchronisation vector
-  involves at most one such action.  This allows us to reuse them as
-  the global actions of the synchronisation vectors, simplifying the
-  translation of properties to be verified (\cf \app{properties}).}
-\noteLH{ce paragraphe sonne vraiment note de rapport de recherche, tu arrives a lui donner un peu d'abstraction/de recul?}
 
@@
 the Algebra of Causal Interaction Trees $\ct(P)$, explicitates the
-causal dependencies discussed above through an encoding mapping
+causal dependencies through an encoding mapping
 $\tau: \ac(P) \rightarrow \ct(P)$.  Another mapping $R: \ct(P)
@@
   \rightarrow
-  \alpha_p
+  {\color{blue}\alpha \bigl(b_p^{p \in P_x}\bigr)}
   \\
@@
 \end{multline}
-%% \noteSB{Ought to group ports by components in
-%%   $\Tuple{p\bigl(\export[A](p),\export[A]'(p),b_p\bigr)}^{p \in P_x}$...
-%%   \newline
-%%   Will probably restrict interactions to one port per component
-%%   throughout the paper to simplify.
-%% }
-%
-with $b_p$ a fresh Boolean variable, $\alpha_p$ a fresh name, $\tau :
+%
+with $b_p^{p \in P_x}$ fresh Boolean variables, $\alpha$ a fresh name, $\tau :
 \ac(P_A) \rightarrow \ct(P_A)$ and $R : \ct(P_A) \rightarrow
@@
 the substitution that replaces in the expression that preceeds it
-all occurrences of $p$ by $b_p$.
+all occurrences of all $p$ by corresponding variables $b_p$.
+
+\addSB{%
+%
+For the sake of clarity, we simplify the encoding in
+\fig{FailureTimer:pNet} by reusing the port names of the original
+architecture instead of fresh names $\alpha$.  This is made
+possible by the fact that each synchronisation vector involves at
+most one action of interest (see the properties in
+\app{properties}).
+%% In the general encoding, the global actions of the
+%% synchronisation vectors should be fresh action names.
+%% However,
+%% for the properties considered in our case study, we only need to
+%% exhibit the actions of the holes.  Furthermore, each
+%% synchronisation vector involves at most one such action.
+%% This
+%% allows us to reuse them as the global actions of the
+%% synchronisation vectors, simplifying the translation of
+%% properties to be verified (\cf \app{properties}).
+%
+}\noteLH{ce
+  paragraphe sonne vraiment note de rapport de recherche, tu
+  arrives a lui donner un peu d'abstraction/de recul?}\noteSB{Est-ce que c'est mieux comme \c{c}a ?}
 
@@
 
-\paragraph{Encoding of the maximal progress priority model}
+\paragraph{Encoding of the maximal progress}
 We only present the key idea, which consists in
@@
 \goesto{p(b_p)} q''$ with $b_p = \true$ in $\nopri[A, \partition]$.
-Then, in the SV guard, we have to check whether \emph{all ports
+In the SV guard, we have to check whether \emph{all ports
   leading to $p$ in the causal tree $\tau(x)$ can be fired} (see
@@
 
-\label{secn:arch:verif}
+%% \label{secn:arch:verif}
 
@@
   \caption{The open Automaton of the Failure Monitor Architecture}
-  \label{schema:ArchFailure:OA}
+  \label{fig:ArchFailure:OA}
 \end{figure}
 
-In \cite{HMZ-FORTE2016QBMZ-AVOCS18}, we have described an algorithm
-and a tool that 
-computes the open automaton encoding the semantics of an open
-pNet. This tool computes open transitions from the combinations of all
-possible behaviours and synchronisation vectors of the pNet, then makes
-use of an SMT engine to check satisfiability of the open transition
-predicates, and minimize the size of the resulting automaton.
+\bigskip\noteSB{J'ai repris ce paragraphe}
+The above encoding provides a mechanism for the symbolic verification
+of architectures using our existing tool
+\cite{HMZ-FORTE2016QBMZ-AVOCS18} to compute the open automaton
+semantics of an open pNet. This tool computes open transitions from
+pLTS behaviours and synchronisation vectors of the pNet, then uses an
+SMT engine to check satisfiability of their predicates, minimizing the
+size of the resulting automaton.
 
@@
 
-In Figure~\ref{schema:ArchFailure:OA} we show the full open automaton
-obtained from our pNet. For reasons of space, we have not shown the
-detail of the open transition, but only the assignments of state
-variables, some usefull parts of the predicates, and the resulting
-action; you can find the full details in 
-Appendix \ref{secn:full-results}. As an example, $OT_3$ is the one
-explained in Example~\ref{Example:TimerOT3} page~\pageref{Example:TimerOT3}
+In \fig{ArchFailure:OA} we show the full open automaton
+obtained from the pNet in \fig{FailureTimer:pNet}.  Due to space limitations, we do not show the
+details of the open transitions, but only the assignments of state
+variables, some useful parts of the predicates, and the resulting
+action; full details can be found in 
+\app{full-results}.
+%
+\noteSB{Removed ``As an example...'', since that \ex{TimerOT3} was
+  simplified and does not correspond to the real OT.}
+%% As an example, $OT_3$ is the one
+%% explained in \ex{TimerOT3} (page~\pageref{ex:TimerOT3}).
 
@@
 possible firing of some interactions (e.g. OT 2 and 3 for
-$fail$). At first sight, it appears the rough behaviour is
+{\PortFail}). At first sight, it appears the rough behaviour is
 reasonable, although a detailed study shows that the property stated
 in page~\pageref{property:reset} does not hold, because of the
-$fail$ loops on states $11$ and $12$. This is because we did not use
-the maximal progress assumption here. If we do, we get the corrected
-behaviour in Fig~\ref{schema:ArchFailure:OA-MaxProgress}
-(\app{full-results}), in which $OT_7$ has 
-disappeared, and $OT_2$ and $OT_{10}$ have been restricted to
-$b0=false$. This one verifies all the properties listed in
-\app{properties}.
+{\PortFail} loops on states $11$ and $12$. This is because we did not
+use the maximal progress assumption here. If we do, we get the
+corrected behaviour in \fig{ArchFailure:OA-MaxProgress}
+(\app{full-results}), in which $OT_7$ has disappeared, and $OT_2$ and
+$OT_{10}$ have been restricted to $b0=\false$. This one verifies all
+the properties listed in \app{properties}.
 
@@
 readability. This comes as a complement to the open automaton in
-Fig. \ref{schema:ArchFailure:OA-annex}, in which we only have a partial view
+\fig{ArchFailure:OA-annex}, in which we only have a partial view
 of the OTs details.
@@
   \caption{The open Automaton of the Failure Monitor Architecture}
-  \label{schema:ArchFailure:OA-annex}
+  \label{fig:ArchFailure:OA-annex}
 \end{figure}
@@
 
-  In Fig. \ref{schema:ArchFailure:OA-annex}, you can see that some
+  In \fig{ArchFailure:OA-annex}, you can see that some
   properties from appendix \app{properties} do not hold.
@@
 
-  The new OA is shown in figure \ref{schema:ArchFailure:OA-MaxProgress}.
+  The new OA is shown in \fig{ArchFailure:OA-MaxProgress}.
 
@@
     with Maximal Progress}
-  \label{schema:ArchFailure:OA-MaxProgress}
+  \label{fig:ArchFailure:OA-MaxProgress}
 \end{figure}
@@
 \bigskip
-Fig. \ref{schema:ArchFailure:OA-TimerV4X2} shows the open automata of
+\Fig{ArchFailure:OA-TimerV4X2} shows the open automata of
 this composed architecture.
@@
   \caption{The open Automaton of the composed system}
-  \label{schema:ArchFailure:OA-TimerV4X2}
+  \label{fig:ArchFailure:OA-TimerV4X2}
 \end{figure}

### 2019-02-19 2018-Arch-pNets/arch-pNets.tex
comments and paragraph title

@@
   paragraphe sonne vraiment note de rapport de recherche, tu
-  arrives a lui donner un peu d'abstraction/de recul?}\noteSB{Est-ce que c'est mieux comme \c{c}a ?}
+  arrives a lui donner un peu d'abstraction/de recul?}\noteSB{Est-ce que c'est mieux comme \c{c}a ? OUI -- Ludo}
 
@@
 
-\bigskip\noteSB{J'ai repris ce paragraphe}
+%\bigskip
+
+\paragraph{Practical experiments.}\noteSB{J'ai repris ce paragraphe}
+\noteLH{j ai nomme ce paragraphe}
 The above encoding provides a mechanism for the symbolic verification
@@
 size of the resulting automaton.
-
 %% The encoding into the SMT language involves the definition of the
@@
 %% as possible (even if it cannot be complete).
-
 %% The resulting open automaton will later be subject to (symbolic)
@@
 %% explained in \ex{TimerOT3} (page~\pageref{ex:TimerOT3}).
-
 This automaton has 12 transitions, including those encoding various
 possible firing of some interactions (e.g. OT 2 and 3 for
-{\PortFail}). At first sight, it appears the rough behaviour is
+{\PortFail}). \add{It looks like} the rough behaviour is
 reasonable, although a detailed study shows that the property stated

### 2019-02-19 2018-Arch-pNets/arch-pNets.tex
intro appendices

@@
 
+\add{The following appendices are included for convenience and would be integrated into a research report if the paper is accepted for publication.
+The first appendices gives complementary informations previously published, while the other appendices provide additional formal details complementing architecture definitions, proofs of theorems, and the case study.}
+
 \section{Algebraic representations of the interaction model}

### 2019-02-19 2018-Arch-pNets/arch-pNets.tex
arch-pNets paper: Minor edits :

--- 2019-02-19 2018-Arch-pNets/arch-pNets.tex
@@
 %
-For the sake of clarity, we simplify the encoding in
+For the sake of clarity, we simplify the case study encoding in
 \fig{FailureTimer:pNet} by reusing the port names of the original
@@
 
-% \subsection{SMT encoding of open pNets}
+%% \subsection{SMT encoding of open pNets}
 % \label{secn:smt}
@@
 
-\paragraph{Practical experiments.}\noteSB{J'ai repris ce paragraphe}
+\paragraph{Practical experiments}\noteSB{J'ai repris ce paragraphe}
 \noteLH{j ai nomme ce paragraphe}
@@
 \clearpage
+
+\noindent
+\add{The following appendices are included for convenience and would be integrated into a research report if the paper is accepted for publication.
+The first appendix provides previously published complementary information, whereas the subsequent ones give additional formal details complementing architecture definitions, proofs of theorems, and the case study.}
 
@@
   \begin{equation*}
-    \AG \bigl(\PortFail(true) \rightarrow \EU[]{\lnot \PortFail(true)}{\PortReset}\bigr).
+    \AG \bigl(\PortFail(true) \rightarrow \EX \EU[]{\lnot \PortFail(true)}{\PortReset}\bigr).
   \end{equation*}

### 2019-02-22 2018-Arch-pNets/arch-pNets.tex
Nettoye presque toutes le notes...

@@
 }$
-\noteEM{Attention, bug dans la figure 2, ou tu mets $reset\mapsto \mathit{zone}$}\noteSB{Done!}respectively.
+%\noteEM{Attention, bug dans la figure 2, ou tu mets $reset\mapsto \mathit{zone}$}\noteSB{Done!}
+respectively.
 %
@@
 
-\addSB{Intuitively, an interaction can be fired if all the involved
+  Intuitively, an interaction can be fired if all the involved
   components are ready to fire their corresponding transitions.  The
@@
   The update assignment of the interaction is executed first, followed
-  by those of the components.}
+  by those of the components.
 
@@
 
-\addSB{In addition to interaction models, BIP relies on 
+In addition to interaction models, BIP relies on 
   \emph{priority models} that impose  a strict partial order on
@@
 obtained results to other priority models.
-}
+
 %% Below, we will assume that the maximal progress priority $\mu$ is
@@
 appropriate logic can be used to specify them.  For instance, the
-property \addSB{\emph{``There is always a possibility to reset the system
+property \emph{``There is always a possibility to reset the system
   after a single failure''} (\ie without
-  additional failures having to occur in the meantime)} enforced by the
-Failure Monitor architecture can be specified using CTL as \noteSB{Removed $\lnot \PortResume$, because not needed \emph{and} could not reformulate nicely in English.}\addSB{$\AG
+  additional failures having to occur in the meantime) enforced by the
+  Failure Monitor architecture can be specified using CTL as
+%  \noteSB{Removed $\lnot \PortResume$, because not needed \emph{and} could not reformulate nicely in English.}
+    $\AG
 \bigl(\PortFail \rightarrow \EX \EU[]{\lnot \PortFail}{
-  \PortReset}\bigr)$}.  Additional properties are provided in
+  \PortReset}\bigr)$.  Additional properties are provided in
 \app{properties}.
@@
 
-\addSB{%
+%\addSB{%
 %
@@
 %
-}
+%}
 
@@
 \PortReset\}\bigr\}$.  This corresponds to the intuition that the
-dangling ports {\PortFail} and {\PortResume} will be provided by a \noteLH{monitored ou monitoring???}
+dangling ports {\PortFail} and {\PortResume} will be provided by a
+%\noteLH{monitored ou monitoring???}
 monitored component, whereas {\PortAsk} and {\PortReset} correspond to
@@
 
-\addSB{We encode all interactions of a connector in one synchronisation vector.  This will allow us to also encode the maximal progress priority model.}
+%\addSB{
+We encode all interactions of a connector in one synchronisation vector.  This will allow us to also encode the maximal progress priority model.
+%}
 We use
@@
 
-\noteEM{Dans le paragraph precedent, tu resume le cas des connecteurs sans data, dans les prochains, tu formalise avec data, mais pour le lecteur ``casual'', le changement n'est pas evident... }
-Below, we assume that, as in \fig{schema:ArchFailure:BIP}, the
+% \noteEM{Dans le paragraph precedent, tu resume le cas des connecteurs sans data, dans les prochains, tu formalise avec data, mais pour le lecteur ``casual'', le changement n'est pas evident... }
+
+Now we lift this encoding to the data-sensitive case. Below, we assume that, as in \fig{schema:ArchFailure:BIP}, the
 interaction model is defined by a set of connectors, annotated with
@@
 architecture $A$ and by $P_x$ the set of ports involved in the
-connector $x \in \gamma$.  Then, \addSB{the interaction model defined by $\gamma$ is 
+connector $x \in \gamma$.  Then,
+%\addSB{
+the interaction model defined by $\gamma$ is 
   $\Gamma = \setdef{(a,g,u)}{(x,g,u) \in \gamma, a \in \intsem{x}}$
-  and the encoding of $\Gamma$ is} $\nopri[\Gamma] \bydef{=}
+and the encoding of $\Gamma$ is
+%}
+$\nopri[\Gamma] \bydef{=}
 \setdef{\nopri[x,g,u]}{(x,g,u) \in \gamma}$, where $\nopri[x,g,u]$ is the synchronisation vector defined by
@@
   \rightarrow
-  {\color{blue}\alpha \bigl(b_p^{p \in P_x}\bigr)}
+  \alpha \bigl(b_p^{p \in P_x}\bigr)
   \\
@@
 %
-}\noteLH{ce
-  paragraphe sonne vraiment note de rapport de recherche, tu
-  arrives a lui donner un peu d'abstraction/de recul?}\noteSB{Est-ce que c'est mieux comme \c{c}a ? OUI -- Ludo}
+%}\noteLH{ce
+  %% paragraphe sonne vraiment note de rapport de recherche, tu
+  %% arrives a lui donner un peu d'abstraction/de recul?}\noteSB{Est-ce que c'est mieux comme \c{c}a ? OUI -- Ludo}
 
@@
 
-\paragraph{Practical experiments}\noteSB{J'ai repris ce paragraphe}
-\noteLH{j ai nomme ce paragraphe}
+\paragraph{Practical experiments.}%\noteSB{J'ai repris ce paragraphe}
+%\noteLH{j ai nomme ce paragraphe}
 The above encoding provides a mechanism for the symbolic verification
@@
 %
-\noteSB{Removed ``As an example...'', since that \ex{TimerOT3} was
-  simplified and does not correspond to the real OT.}
+%\noteSB{Removed ``As an example...'', since that \ex{TimerOT3} was
+%  simplified and does not correspond to the real OT.}
 %% As an example, $OT_3$ is the one
@@
 possible firing of some interactions (e.g. OT 2 and 3 for
-{\PortFail}). \add{It looks like} the rough behaviour is
+{\PortFail}). It looks like the rough behaviour is
 reasonable, although a detailed study shows that the property stated
@@
 \noindent
-\add{The following appendices are included for convenience and would be integrated into a research report if the paper is accepted for publication.
-The first appendix provides previously published complementary information, whereas the subsequent ones give additional formal details complementing architecture definitions, proofs of theorems, and the case study.}
+%\add{
+The following appendices are included for convenience and would be integrated into a research report if the paper is accepted for publication.
+The first appendix provides previously published complementary information, whereas the subsequent ones give additional formal details complementing architecture definitions, proofs of theorems, and the case study.
+%}
 
@@
 
+\bigskip
 \noindent
@@
 \end{verbatim}
+\bigskip
 
@@
 
+\bigskip
 \verbatimfont{\small}
@@
 
-\medskip
+\bigskip
 \noindent
@@
 
-  \subsubsection{Properties}
+  \paragraph{Properties.}
 
@@
 
+\bigskip
 \small\begin{verbatim}
@@
 
+\bigskip
 \begin{verbatim}
@@
 
-\subsubsection{Scaling-up: composing architectures}
-
-\medskip
+\subsubsection{Scaling-up: composing architectures.}
 
@@
 
-\medskip
+\bigskip
 \begin{verbatim}
@@
 
-  \begin{figure}[h]
+  \begin{figure}[t]
   \centering

### 2019-02-22 2018-Arch-pNets/arch-pNets.tex
presque pret...
arch-pNets paper: Clean-up before intermediate submission to Coordination '19

@@
 $\false$.
-\noteLH{enleve le 3 et integre au 2}
+%% \noteLH{enleve le 3 et integre au 2}
 Formally,  $\nopri[C] \bydef{=} \pNetTuple{S, s_0, \goesto[{\nopri[C]}]{}}$, such that
@@
 \item $s_0 \not\in Q_C$ is fresh and $S = Q_C \cup \{s_0\}$,
-  \noteEM{En principe les $vars(s)$ devraient etre disjoints, mais je
-    veux bien laisser ca sous le tapis tant qu'on n'implemente pas le codage...}
+  %% \noteEM{En principe les $vars(s)$ devraient etre disjoints, mais je
+  %%   veux bien laisser ca sous le tapis tant qu'on n'implemente pas le codage...}
 \item $\vars(s) = V_C \cup \setdef{?x'}{x \in \export[C](p), p \in a, s\goesto{a} }$, for all $s \in Q_C$, and $\vars(s_0) =
@@
 \item let  $\mathit{uinit} \bydef{=} \bigl(x := \val{0}{C}(x)\bigr)^{x \in V_C}$ and,
-  \noteSB{Ludo, Eric, pourriez-vous v\'erifier que cela est
-    compr\'ehensible ? Ok pour moi (Eric) OK Ludo, rephrase un peu}%
-  \add{for all $s \goesto{a, g, u} s'$ with $u = (x\! :=
+  %% \noteSB{Ludo, Eric, pourriez-vous v\'erifier que cela est
+  %%   compr\'ehensible ? Ok pour moi (Eric) OK Ludo, rephrase un peu}
+  %
+  for all $s \goesto{a, g, u} s'$ with $u = (x\! :=
 \! e_x)^{x
@@
 %
-\noteEM{j'ai inverse les $\export[C]'(a), \export[C](a)$ dans les
-  actions, pour etre conforme a la notation de la Def 1 page 4. }
+%% \noteEM{j'ai inverse les $\export[C]'(a), \export[C](a)$ dans les
+%%   actions, pour etre conforme a la notation de la Def 1 page 4. }
 \begin{multline*}
@@
     {} \cup \bigl\{(s_0, \init, \true, \mathit{uinit}, q^0_C)\bigr\}.
-  \end{multline*}}
-\end{itemize}\vspace{-3ex}
+  \end{multline*}
+\end{itemize}%\vspace{-3ex}
 
@@
 the algorithms, for large case-studies
-(e.g. \cite{DBLP:journals/corr/CimattiGMT13,DBLP:journals/corr/abs-1806-11459}). Also 
+(e.g. \cite{DBLP:journals/corr/CimattiGMT13,DBLP:journals/corr/abs-1806-11459}). %% Also
+
 %% SMT on an application not using component structure. is there a strong Z3 example == Eric
@@
 
-  Denoting \todoSB{One tilde is enough}$\val[\doubletilde]{}{1}$ the restriction of
+  Denoting %% \todoSB{One tilde is enough}
+  $\val[\doubletilde]{}{1}$ the restriction of
 %
@@
   $(\val[\primeit]{}{1}, \val[\primeit]{}{}) \order
-  \val[\doubletilde]{}{1}[e^1; (e_1, e_b)]$.  \todoSB{Remove this}\hl{Notice that all
-  variables affected by both $e^1$ and $e^2$ must necessarily
-  belong to $\bigcup_{B \in \cB} V_B$.}  Hence,
+  \val[\doubletilde]{}{1}[e^1; (e_1, e_b)]$.  %% \todoSB{Remove this}\hl{Notice that all
+  %% variables affected by both $e^1$ and $e^2$ must necessarily
+  %% belong to $\bigcup_{B \in \cB} V_B$.}
+  Hence,
 %
@@
 reset. This is because without priorities we can have an
-activity on the dandling ``fail'' port without synchronising with the
+activity on the dangling ``fail'' port without synchronising with the
 others, even if they are available.
@@
 
-\subsubsection{Scaling-up: composing architectures.}
-
-Here is the code of the corresponding composed pNet:
-\noteEMin{Il faudrait (mais a-t-on le temps?): faire un dessin de la
-  composition au niveau BIP, et au niveau pNet. Un resultat brut, vaguement
-  correct, montre 37 OTs, modulo les petites questions de mon mail de
-  mercredi midi...}
-
-\todoSBin{Ecrire les proprietes qu'il doit verifier... ? }
-
-\bigskip
-\begin{verbatim}
-SV0: <tick(z, t, z1), fail(zone1, b11), fail(zone2, b12), fail1(b01), fail2(b02), _> 
-     --> fail(b01, b02), 
-     [(z1 = z |Intersection| ((b11?zone1:TopInt)+t) |Intersection| ((b12?zone2:TopInt)+t))
-      /\(b11=>b01)/\(b12=>b02)]
-SV1: <cancel(b1), resume(b21), resume(b22), resume1, resume2, _>-->resume, 
-     [(b1=b21)/\(b1=b22)]
-SV2: <timeout, timeout, timeout, _, _, ask>-->ask
-SV3: <_, reset, reset, _, _, reset>-->reset
-SV4: <init, init, init, _, _, _>-->init
-
-pLTS: Timer
-- Transition: t0---init-->t1, { t := 0 z := TopInt}
-- Transition: t1---tick(z, t, z1)-->t1, [t<(GET_MAX z)], { t := t+1 z := z1}
-- Transition: t1---cancel(false)-->t1, {}
-- Transition: t1---cancel(true)-->t1, { t := 0 z := TopInt}
-- Transition: t1---timeout-->t1, [t in z], { t := 0 z := TopInt}
-
-pLTS: FC1
-- Transition: s0---init-->s1, { zone1 := minZone1,maxZone1}
-- Transition: s1---timeout-->s1, {}
-- Transition: s1---resume(false)-->s1, {}
-- Transition: s1---fail(zone1, false)-->s1, {}
-- Transition: s1---fail(zone1, true)-->s2, {}
-- Transition: s2---fail(zone1, false)-->s2, {}
-- Transition: s2---resume(false)-->s2, {}
-- Transition: s2---resume(true)-->s1, {}
-- Transition: s2---timeout-->s3, {}
-- Transition: s3---fail(zone1, false)-->s3, {}
-- Transition: s3---timeout-->s3, {}
-- Transition: s3---resume(false)-->s3, {}
-- Transition: s3---reset-->s1, {}
-
-pLTS: FC2
-- Transition: s0---init-->s1, { zone2 := minZone2,maxZone2}
-- Transition: s1---timeout-->s1, {}
-- Transition: s1---resume(false)-->s1, {}
-- Transition: s1---fail(zone2, false)-->s1, {}
-- Transition: s1---fail(zone2, true)-->s2, {}
-- Transition: s2---fail(zone2, false)-->s2, {}
-- Transition: s2---resume(false)-->s2, {}
-- Transition: s2---resume(true)-->s1, {}
-- Transition: s2---timeout-->s3, {}
-- Transition: s3---fail(zone2, false)-->s3, {}
-- Transition: s3---timeout-->s3, {}
-- Transition: s3---resume(false)-->s3, {}
-- Transition: s3---reset-->s1, {}
-
-INFO  BIPArchFailureTimerMaxV4X2 - Total: 37 SATISFIABLE OTs
-INFO  BIPArchFailureTimerMaxV4X2 -        3136 UNSATISFIABLE OTs
-INFO  BIPArchFailureTimerMaxV4X2 - Total Time: 9111 ms
-\end{verbatim}
-
-\bigskip
-\Fig{ArchFailure:OA-TimerV4X2} shows the open automata of
-this composed architecture.
-Note that e..g. the open transition labelled ``$fail(*,tt)$'' stands for
-``$fail(b01,b02)$'', where  $b01'$ can be arbitrarily true or
-false. As in the previous case, this is because we have not use here
-the Max Progress hypothesis, otherwise all the ``*'' in the figure
-should be replaced by ``$ff$''.
-
-  \begin{figure}[t]
-  \centering
-  \includegraphics[width=0.8\columnwidth]{TimerV4X2}
-  \caption{The open Automaton of the composed system}
-  \label{fig:ArchFailure:OA-TimerV4X2}
-\end{figure}
+%% \subsubsection{Scaling-up: composing architectures.}
+
+%% Here is the code of the corresponding composed pNet:
+%% %% \noteEMin{Il faudrait (mais a-t-on le temps?): faire un dessin de la
+%% %%   composition au niveau BIP, et au niveau pNet. Un resultat brut, vaguement
+%% %%   correct, montre 37 OTs, modulo les petites questions de mon mail de
+%% %%   mercredi midi...}
+
+%% %% \todoSBin{Ecrire les proprietes qu'il doit verifier... ? }
+
+%% \bigskip
+%% \begin{verbatim}
+%% SV0: <tick(z, t, z1), fail(zone1, b11), fail(zone2, b12), fail1(b01), fail2(b02), _> 
+%%      --> fail(b01, b02), 
+%%      [(z1 = z |Intersection| ((b11?zone1:TopInt)+t) |Intersection| ((b12?zone2:TopInt)+t))
+%%       /\(b11=>b01)/\(b12=>b02)]
+%% SV1: <cancel(b1), resume(b21), resume(b22), resume1, resume2, _>-->resume, 
+%%      [(b1=b21)/\(b1=b22)]
+%% SV2: <timeout, timeout, timeout, _, _, ask>-->ask
+%% SV3: <_, reset, reset, _, _, reset>-->reset
+%% SV4: <init, init, init, _, _, _>-->init
+
+%% pLTS: Timer
+%% - Transition: t0---init-->t1, { t := 0 z := TopInt}
+%% - Transition: t1---tick(z, t, z1)-->t1, [t<(GET_MAX z)], { t := t+1 z := z1}
+%% - Transition: t1---cancel(false)-->t1, {}
+%% - Transition: t1---cancel(true)-->t1, { t := 0 z := TopInt}
+%% - Transition: t1---timeout-->t1, [t in z], { t := 0 z := TopInt}
+
+%% pLTS: FC1
+%% - Transition: s0---init-->s1, { zone1 := minZone1,maxZone1}
+%% - Transition: s1---timeout-->s1, {}
+%% - Transition: s1---resume(false)-->s1, {}
+%% - Transition: s1---fail(zone1, false)-->s1, {}
+%% - Transition: s1---fail(zone1, true)-->s2, {}
+%% - Transition: s2---fail(zone1, false)-->s2, {}
+%% - Transition: s2---resume(false)-->s2, {}
+%% - Transition: s2---resume(true)-->s1, {}
+%% - Transition: s2---timeout-->s3, {}
+%% - Transition: s3---fail(zone1, false)-->s3, {}
+%% - Transition: s3---timeout-->s3, {}
+%% - Transition: s3---resume(false)-->s3, {}
+%% - Transition: s3---reset-->s1, {}
+
+%% pLTS: FC2
+%% - Transition: s0---init-->s1, { zone2 := minZone2,maxZone2}
+%% - Transition: s1---timeout-->s1, {}
+%% - Transition: s1---resume(false)-->s1, {}
+%% - Transition: s1---fail(zone2, false)-->s1, {}
+%% - Transition: s1---fail(zone2, true)-->s2, {}
+%% - Transition: s2---fail(zone2, false)-->s2, {}
+%% - Transition: s2---resume(false)-->s2, {}
+%% - Transition: s2---resume(true)-->s1, {}
+%% - Transition: s2---timeout-->s3, {}
+%% - Transition: s3---fail(zone2, false)-->s3, {}
+%% - Transition: s3---timeout-->s3, {}
+%% - Transition: s3---resume(false)-->s3, {}
+%% - Transition: s3---reset-->s1, {}
+
+%% INFO  BIPArchFailureTimerMaxV4X2 - Total: 37 SATISFIABLE OTs
+%% INFO  BIPArchFailureTimerMaxV4X2 -        3136 UNSATISFIABLE OTs
+%% INFO  BIPArchFailureTimerMaxV4X2 - Total Time: 9111 ms
+%% \end{verbatim}
+
+%% \bigskip
+%% \Fig{ArchFailure:OA-TimerV4X2} shows the open automata of
+%% this composed architecture.
+%% Note that e..g. the open transition labelled ``$fail(*,tt)$'' stands for
+%% ``$fail(b01,b02)$'', where  $b01'$ can be arbitrarily true or
+%% false. As in the previous case, this is because we have not use here
+%% the Max Progress hypothesis, otherwise all the ``*'' in the figure
+%% should be replaced by ``$ff$''.
+
+%%   \begin{figure}[t]
+%%   \centering
+%%   \includegraphics[width=0.8\columnwidth]{TimerV4X2}
+%%   \caption{The open Automaton of the composed system}
+%%   \label{fig:ArchFailure:OA-TimerV4X2}
+%% \end{figure}
 

### 2019-02-25 2018-Arch-pNets/arch-pNets.tex

@@
 model  that supports SMT-based verification.
-Additionally, the translation into  open pNet  gives
+Additionally, the translation into  open pNet  \noteEM{ICI}{gives
 us a strong insight and a comparison of the coordination mechanisms
-provided by the two frameworks.  The approach is illustrated by a case
+provided by the two frameworks}.  The approach is illustrated by a case
 study based on a previously developed BIP model of a nanosatellite
@@
 Due to the nature of the problem, we propose to rely on a translation of BIP architectures into pNets, a direct verification of BIP could  be possible but pNets already have verification tools based on a SMT solver, and doing the same work for BIP would require  a large amount of similar development.
-More interestingly, relying on a translation to pNets allows us to compare the two models.
+More interestingly, relying on a translation to pNets \noteEM{LA}{allows us to compare the two models}.
 
@@
 compare BIP architectures and  pNet formalism.  
-Overall, the encoding allows us to precisely compare the coordination
+Overall, the encoding \noteEM{ET LA}{allows us to precisely compare the coordination
 mechanisms of the two models but also the way component composition is
-expressed in the two formalisms. 
+expressed in the two formalisms}. 
 %This also gives the opportunity

### 2019-02-26 2018-Arch-pNets/arch-pNets.tex
arch-pNets paper: revised introduction, related work and conclusion; run a spell checker.

--- 2019-02-22 2018-Arch-pNets/arch-pNets.tex
@@
 \newcommand{\secn}[1]{Sect.~\ref{secn:#1}}
+\newcommand{\Secn}[1]{Section~\ref{secn:#1}}
 \newcommand{\app}[1]{App.~\ref{secn:#1}}
@@
 model  that supports SMT-based verification.
-Additionally, the translation into  open pNet  gives
-us a strong insight and a comparison of the coordination mechanisms
-provided by the two frameworks.  The approach is illustrated by a case
+%% Additionally, the translation into  open pNet  \noteEM{ICI}{gives
+%% us a strong insight and a comparison of the coordination mechanisms
+%% provided by the two frameworks}.
+The approach is illustrated by a case
 study based on a previously developed BIP model of a nanosatellite
@@
 application of architectures is compositional \wrt safety properties,
-\ie if two architectures guarantee two properties, their composition ensure the conjunction of the properties.
+\ie if two architectures guarantee two properties, their composition ensures the conjunction of the properties.
 %
@@
 it is necessary to have a representation of the BIP architecture in a verifiable format. 
-The verification problem has two unbounded parameters: 1) By nature, architectures have holes and are meant to interact with the interfaces of the component that will fill the hole; the properties must hold for all (well-typed) components that can be put inside the hole; 2) BIP interactions can transmit data, and properties might be dependent of the data, the domain of the data is generally huge or unbound and the value of transmitted data might have a significant impact on the properties.
-Due to the nature of the problem, we propose to rely on a translation of BIP architectures into pNets, a direct verification of BIP could  be possible but pNets already have verification tools based on a SMT solver, and doing the same work for BIP would require  a large amount of similar development.
-More interestingly, relying on a translation to pNets allows us to compare the two models.
-
-Parameterised Networks of synchronised automata (pNets) is a formalism for defining behavioural specification of distributed systems based on a parametrised and hierarchical model.
+The verification problem has two unbounded parameters: 1) By nature, architectures have holes and are meant to interact with the interfaces of the component that will fill the hole; the properties must hold for all (well-typed) components that can be put inside the hole; 2) BIP interactions can transmit data, and properties might be dependent of the data, the domain of the data is generally huge or unbounded and the values of transmitted data might have a significant impact on the properties.
+%% Due to the nature of the problem, 
+We propose to rely on a translation of BIP architectures into \emph{open pNets}.
+
+Parameterised Networks of synchronised automata (pNets) is a formalism for defining behavioural specification of distributed systems based on a parameterised and hierarchical model.
 It inherited from the work of
 Arnold on synchronisation vectors~\cite{Arnold1982}. 
-It has been shown work~\cite{HMZ:PDP15} that pNets can  represent the behavioural semantics
+It has been shown in previous work~\cite{HMZ:PDP15} that pNets can  represent the behavioural semantics
 of a system 
@@
 \cite{CM:FMCO08,HKM-FASE16}. 
-pNets structure is static, but unbounded,  this allows for model-checking
+The structure of pNets is static but unbounded.  This allows for model-checking
 approaches even for reconfigurable applications.
@@
 parameters. Such open systems can represent composition operators or structuring architectures.
-It is possible to reason, in an SMT engine, on the symbolic automaton that represents the behaviour of a pNets with holes and that communicates value~\cite{HMZ-FORTE2016QBMZ-AVOCS18}.
-This encoding of open pNets into Z3 that is under development is the starting point of this article.
+It is possible to reason, in an SMT engine, on the symbolic automaton that represents the behaviour of a pNets with holes and that communicates values~\cite{HMZ-FORTE2016QBMZ-AVOCS18}.
+The encoding of open pNets into Z3 that is under development is the starting point of this article.
 We benefit from the possibility to reason on a pNet in an SMT engine in order to prove properties on BIP architectures.
 
-We propose   to encode BIP architectures
-into open pNets and to verify, using SMT techniques,
-the properties of the architectures. The encoding also allows us to
-compare BIP architectures and  pNet formalism.  
-Overall, the encoding allows us to precisely compare the coordination
-mechanisms of the two models but also the way component composition is
-expressed in the two formalisms. 
+%% We propose   to encode BIP architectures
+%% into open pNets and to verify, using SMT techniques,
+%% the properties of the architectures. The encoding also allows us to
+%% compare BIP architectures and  pNet formalism.  
+%% Overall, the encoding allows us to precisely compare the coordination
+%% mechanisms of the two models but also the way component composition is
+%% expressed in the two formalisms.
+
 %This also gives the opportunity
@@
 nanosatellite on-board software~\cite{CubETH-case-study}.
+%
+This running example also relies on the \emph{maximal progress}
+assumption, whereby larger interactions are preferred to smaller
+ones.  Due to space limitations, we only discuss this
+informally. However, proofs of the results provided in the
+appendix formally account for maximal progress.
+
+The rest of the paper is structured as follows.  In
+\secn{preliminaries}, we present notations and background
+material on pNets.  The theory of architectures with data is
+presented in \secn{archs}.  In \secn{encoding}, we present the
+encoding into open pNets and discuss verification of the running
+example.  \Secn{related} discusses related work.
+\Secn{conclusion} concludes the paper.
 
@@
 expressions} 
-$\boolexprs{\variables}\subseteq\exprs{\variables}$, $g$ (guards) ranges over boolean expressions.
+$\boolexprs{\variables}\subseteq\exprs{\variables}$, $g$ (guards) ranges over Boolean expressions.
 On top of $\exprs{\variables}$ we build the \emph{action algebra}
@@
 %on the finite branching of the transition relation.
-Variables of each state are parwise disjoint.
+Variables of each state are pairwise disjoint.
 We need to introduce input variables to reason about the data flow between actions.
 We  define the set of parameterised actions a pLTS can use ($a$
-ranges over action labels):\\
+ranges over action labels):
 % Action terms are  of the form 
@@
   An \emph{open transition} over a
-	set $J$ of holes  and a set of states $\mathcal{S}$ is 
-	a structure of the form:
-\\[-2ex]	
-	\begin{mathpar}
-	\inferrule*[myfraction=\reddottedrule]
+  set
+
+  \noindent
+  \begin{tabular}[b]{@{}p{0.86\columnwidth}c{}@{}}
+    of holes $J$ and a set of states $\mathcal{S}$ is a structure
+    of the form to the right,
+%
+    &
+%
+    %% \\[-2ex]	
+    %% \begin{mathpar}
+    \raisebox{1mm}[0pt]{
+      $\inferrule*[myfraction=\reddottedrule]
       {	\beta_j^{j\in J}, \Pred, \Post}
-	{s \OTarrow {{\alpha}}s'}
-	\end{mathpar}
-	Where $s, s'\in\mathcal{S}$ and $\beta_j\in\actions{\variables}$
-        is an action of the hole $j$. $\alpha$ is the resulting global action. \Pred\ is a predicate 
-	over the different variables of the
-	terms, labels, and states  $\beta_j$, $s$, $\alpha$. $\Post\in 
-	\assigns{\variables}$\ is 
-	a set of assignments that are the effects of the transition.
-Open transitions are identified modulo logical equivalence on their predicate.
+      {s \OTarrow {{\alpha}}s'}$
+      }
+    %% \end{mathpar}
+%
+    \\
+%
+    \multicolumn{2}{p{\columnwidth}}{%
+%
+    where $s, s'\in\mathcal{S}$;
+    $\beta_j\in\actions{\variables}$ is an action of the hole
+    $j$; $\alpha$ is the resulting global action; {\Pred} is a
+    predicate over the different variables of the terms, labels,
+    and states $\beta_j$, $s$, $\alpha$; and $\Post\in
+    \assigns{\variables}$ is a set of assignments that are the
+    effects of the transition.  Open transitions are identified
+    modulo logical equivalence on their predicate.
+%
+    }
+  \end{tabular}
 \end{definition}
@@
 \tstate{0} and \cstate{0}, and valuations $\val{0}{\NameTimer} = \{t
-\mapsto 0, z \mapsto \topinterval\}$
+\mapsto 0, z \mapsto \topinterval\}$,
 $\val{0}{\NameCtrl} =
@@
 \Thm{combining} implies that safe BIP systems can be designed
-\emph{compositionally}.  Indeed, it is sufficient to verify that
+\emph{compositionally}:  it is sufficient to verify that
 1)~the applied architectures do enforce their characteristic
-properties and 2)~that they are pairwise upwards compatible.  To
-a large extent, item~2, \ie verification of the upwards
-compatibility, can be carried out syntactically by analysing the
-structure of the connectors defining the interaction models:
-maximal progress is mostly relevant for connectors involving
-triggers; whenever a trigger port is not common to both
-architectures, upwards \emph{in}compatibility cannot arise.  The
+properties and 2)~they are pairwise upwards compatible.  To
+a large extent, %% item~2, \ie verification of the upwards
+%% compatibility,
+the latter
+can be carried out syntactically by analysing the
+structure of the connectors that define the interaction models.
+%% maximal progress is mostly relevant for connectors involving
+%% triggers; whenever a trigger port is not common to both
+%% architectures, upwards \emph{in}compatibility cannot arise.
+The
 next section is devoted to the encoding of architectures into
-pNets, which addresses item~1 by symbolic verification.
+pNets, addressing item~1 by symbolic verification.
 %
@@
 $\init$ transition that initialises all the variables to those defined
-by the initial valuation $\val{0}{C}$ of $C$, 2)~an action algebra that matches the actions of the coordinator ports but adds, an additional boolean action parameter, and also, for each exported
+by the initial valuation $\val{0}{C}$ of $C$, 2)~an action algebra that matches the actions of the coordinator ports but adds, an additional Boolean action parameter, and also, for each exported
 variable $x$, a corresponding fresh input variable $?x'$ to allow updates during interactions, 3)~pLTS transitions that reflect the original transitions of
@@
   \includegraphics[width=0.9\columnwidth]{FailureTimerPNET-v4}
-  \caption{The open pNET encoding the Failure Monitor architecture (\fig{schema:ArchFailure:BIP}) without the Max Progress priority model}
+  \caption{The open pNet encoding the Failure Monitor architecture (\fig{schema:ArchFailure:BIP}) without the Max Progress priority model}
   \label{fig:FailureTimer:pNet}
@@
 $\NameCtrl.\PortFail\ ?\ \NameCtrl.\mathit{zone} : \topinterval$ in
-the update assignement
+the update assignment
 $
@@
   $\Gamma = \setdef{(a,g,u)}{(x,g,u) \in \gamma, a \in \intsem{x}}$
-and the encoding of $\Gamma$ is
+and the set of synchronisation vectors encoding $\Gamma$ is
 %}
 $\nopri[\Gamma] \bydef{=}
-\setdef{\nopri[x,g,u]}{(x,g,u) \in \gamma}$, where $\nopri[x,g,u]$ is the synchronisation vector defined by
+\setdef{\nopri[x,g,u]}{(x,g,u) \in \gamma}$, with %% $\nopri[x,g,u]$ is the  defined by
 %
@@
 illustrated in \tab{connectors}, $\bigl[\nicefrac{b_p}{p}\bigr]$ is
-the substitution that replaces in the expression that preceeds it
+the substitution that replaces in the expression that precedes it
 all occurrences of all $p$ by corresponding variables $b_p$.
@@
 pLTS behaviours and synchronisation vectors of the pNet, then uses an
-SMT engine to check satisfiability of their predicates, minimizing the
+SMT engine to check satisfiability of their predicates, minimising the
 size of the resulting automaton.
@@
 \label{secn:related}
-Previous works on pNets and BIP architectures have been mentioned at the beginning of the paper.
+%% Aside from previous work on pNets and BIP architectures mentioned in \secn{introduction}.
 We  review here the closest related works outside the scope of pNets and BIP architectures, with a particular focus on compositional and parameterized verification.
@@
 
-Basic research on behaviour models and verification algorithms for
+The design methodology based on BIP architectures
+is inspired by the notion of design patterns introduced
+in~\cite{gamma94-patterns}.  It is radically different
+insofar as BIP architectures posses formal semantics; their
+composition is well defined and preserves their characteristic
+properties.  This is a relatively novel trend with few comparable
+works, whereof the most relevant is a theory formalising common
+architectural styles, such as \emph{publisher-subscriber} or
+\emph{blackboard}, proposed in \cite{Marmsoler14,Marmsoler18}.
+
+Although direct verification of BIP models is possible
+\cite{Lacra15,DFinder,DFinder2,atva15,wang2015verification}, none of
+these previous works address
+compositional verification of parameterised BIP systems with data
+and maximal progress priorities achieved in the present paper.
+
+From a broader perspective,
+basic research on behaviour models and verification algorithms for
 data-sensitive systems started in the nineties, with the seminal work
-of Hennesy, Lin, and their colleagues on value-passing systems with
+of Hennessy, Lin, and their colleagues on value-passing systems with
 assignments
-\cite{CONCUR::Lin1996,HennessyL1995:353,APSEC::Lin2001}. Later, many
+\cite{HennessyL1995:353,CONCUR::Lin1996,APSEC::Lin2001}. Later, many
 different works addressing various classes of infinite-state systems
-and/or paramaterized topologies have been published, using
+and/or parameterised topologies have been published, using
 combinations of approaches, often including predicate abstraction and
-SMT satisfiability (see
-e.g. \cite{BruniEtAl-Tiles-Concur2000,DBLP:conf/cade/GhilardiNRZ08,DBLP:journals/jsat/AlbertiGPRR12,CimattiEtAl-NUXMV-CAV2014,ChampionEtAl-Kind2-CAV2016}). With
+SMT satisfiability (\eg \cite{DBLP:journals/jsat/AlbertiGPRR12,BruniEtAl-Tiles-Concur2000,CimattiEtAl-NUXMV-CAV2014,ChampionEtAl-Kind2-CAV2016,DBLP:conf/cade/GhilardiNRZ08}). With
 respect to these, we use symbolic representations not only to get a
@@
 the algorithms, for large case-studies
-(e.g. \cite{DBLP:journals/corr/CimattiGMT13,DBLP:journals/corr/abs-1806-11459}). %% Also
+(\eg \cite{DBLP:journals/corr/abs-1806-11459,DBLP:journals/corr/CimattiGMT13}). %% Also
 
@@
 As compositional proof of safety is difficult, some approaches rely on theorem proving to ensure the safety of component operations.
-Coqots and Pycots~\cite{BCDLM:CBSE2014} even manage to prove the safety of reconfiguration procedures which are known to be highly difficult to verify, and massively parametrised.
+Coqots and Pycots~\cite{BCDLM:CBSE2014} even manage to prove the safety of reconfiguration procedures which are known to be highly difficult to verify, and massively parameterised.
 The approach relies on a high expertise and significant efforts from the user.
@@
 %****************************************************************
-
 %****************************************************************
@@
 As a result, we obtain automatic and compositional guarantees of safety properties with data where compositionality is given by the BIP architectures, and pNet tools provide automatic verification of the properties of each architecture.
-%
+
+The translational approach allows us to benefit from the methods
+and tools developed separately in BIP and pNets communities,
+avoiding the additional effort of designing the corresponding
+tools in both contexts from scratch.
+
 %The automatic checking of properties given by the pNet framework
@@
     $a \cap P_{C_i} = \emptyset$ and $q_i = q_i'$
-    (for covenience, we put $g_{C_i} = \true$ and $e_{C_i} = \noop$ in item~\ref{aux1} below);
+    (for convenience, we put $g_{C_i} = \true$ and $e_{C_i} = \noop$ in item~\ref{aux1} below);
   \item for $j \in J$,\\
@@
     $a \cap P_{B_j} = \emptyset$ and $q_j = q_j'$
-    (for covenience, we put $g_{B_j} = \true$ and $e_{B_j} = \noop$ in item~\ref{aux1} below);
+    (for convenience, we put $g_{B_j} = \true$ and $e_{B_j} = \noop$ in item~\ref{aux1} below);
   \item\label{ab:end}\label{aux1} $g' = g \land \bigwedge_{i \in I} g_{C_i} \land
@@
     for all $i \in [1,m]$
-    (for covenience, we put $g_{C'} = \true$ and $e_{C'} = \noop$ in
+    (for convenience, we put $g_{C'} = \true$ and $e_{C'} = \noop$ in
     item~\ref{aux2} below);
@@
     $a \cap P_{B_j} = \emptyset$ and $q_j = q_j'$
-    (for covenience, we put $g_{B_j} = \true$ and $e_{B_j} = \noop$ in
+    (for convenience, we put $g_{B_j} = \true$ and $e_{B_j} = \noop$ in
     item~\ref{aux2} below);
@@
     $a \cap P_{C_i} = \emptyset$ and $q_i = q_i'$,
-    (for covenience, we put $g_{C_i} = \true$ and $e_{C_i} = \noop$ in
+    (for convenience, we put $g_{C_i} = \true$ and $e_{C_i} = \noop$ in
     item~\ref{aux3} below);
@@
 
-This can be sloved by the version with the Max Progress encoding.
+This can be solved by the version with the Max Progress encoding.
 This modifies both the pLTS transitions, and the synchronisation

### 2019-02-26 2018-Arch-pNets/arch-pNets.tex
biblio compactee

@@
   An \emph{open transition} over a
-  set
-
-  \noindent
-  \begin{tabular}[b]{@{}p{0.86\columnwidth}c{}@{}}
-    of holes $J$ and a set of states $\mathcal{S}$ is a structure
-    of the form to the right,
-%
-    &
-%
-    %% \\[-2ex]	
-    %% \begin{mathpar}
-    \raisebox{1mm}[0pt]{
-      $\inferrule*[myfraction=\reddottedrule]
+  set of holes $J$  and a set of states $\mathcal{S}$ is 
+       a structure of the form:
+\\[-2ex]       
+       \begin{mathpar}
+       \inferrule*[myfraction=\reddottedrule]
        {       \beta_j^{j\in J}, \Pred, \Post}
-      {s \OTarrow {{\alpha}}s'}$
-      }
-    %% \end{mathpar}
-%
-    \\
-%
-    \multicolumn{2}{p{\columnwidth}}{%
-%
-    where $s, s'\in\mathcal{S}$;
-    $\beta_j\in\actions{\variables}$ is an action of the hole
-    $j$; $\alpha$ is the resulting global action; {\Pred} is a
-    predicate over the different variables of the terms, labels,
-    and states $\beta_j$, $s$, $\alpha$; and $\Post\in
-    \assigns{\variables}$ is a set of assignments that are the
-    effects of the transition.  Open transitions are identified
-    modulo logical equivalence on their predicate.
-%
-    }
-  \end{tabular}
+       {s \OTarrow {{\alpha}}s'}
+       \end{mathpar}
+       Where $s, s'\in\mathcal{S}$ and $\beta_j\in\actions{\variables}$
+        is an action of the hole $j$. $\alpha$ is the resulting global action. \Pred\ is a predicate 
+       over the different variables of the
+       terms, labels, and states  $\beta_j$, $s$, $\alpha$. $\Post\in 
+       \assigns{\variables}$\ is 
+       a set of assignments that are the effects of the transition.
+Open transitions are identified modulo logical equivalence on their predicate.
+%%   \noindent
+%%   \begin{tabular}[b]{@{}p{0.86\columnwidth}c{}@{}}
+%%     of holes $J$ and a set of states $\mathcal{S}$ is a structure
+%%     of the form to the right,
+%% %
+%%     &
+%% %
+%%     %% \\[-2ex]	
+%%     %% \begin{mathpar}
+%%     \raisebox{1mm}[0pt]{
+%%       $\inferrule*[myfraction=\reddottedrule]
+%%       {	\beta_j^{j\in J}, \Pred, \Post}
+%%       {s \OTarrow {{\alpha}}s'}$
+%%       }
+%%     %% \end{mathpar}
+%% %
+%%     \\
+%% %
+%%     \multicolumn{2}{p{\columnwidth}}{%
+%% %
+%%     where $s, s'\in\mathcal{S}$;
+%%     $\beta_j\in\actions{\variables}$ is an action of the hole
+%%     $j$; $\alpha$ is the resulting global action; {\Pred} is a
+%%     predicate over the different variables of the terms, labels,
+%%     and states $\beta_j$, $s$, $\alpha$; and $\Post\in
+%%     \assigns{\variables}$ is a set of assignments that are the
+%%     effects of the transition.  Open transitions are identified
+%%     modulo logical equivalence on their predicate.
+%% %
+%%     }
+%%   \end{tabular}
 \end{definition}

### 2019-03-04 2017-Xudong-SMT/AVOCS-2018-postproc.tex
version Post Proceedings, soumise.

--- 2018-05-26 2017-Xudong-SMT/AVOCS-2018-pre-proceeding.tex
@@
 
-\documentclass{lncs/llncs}
+\documentclass{eceasst}
 \usepackage{etex}
@@
 %\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
-\usepackage{graphicx}
+
+%%\usepackage{graphicx}
 
@@
 %\usepackage{indentfirst}
-\usepackage{amsmath,amssymb,amscd,mathrsfs}
+%%%\usepackage{amsmath,amssymb,amscd,mathrsfs}
 % \usepackage{array,booktabs,arydshln,xcolor}
-\usepackage{array,booktabs,xcolor}
+%
+\usepackage{array,booktabs}
 \DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
-\usepackage{epsfig,color,enumitem}
+%\usepackage{epsfig,color,enumitem}
+\usepackage{epsfig,enumitem}
 \usepackage[%
@@
 
-\usepackage{hyperref}
+%%\usepackage{hyperref}
 \usepackage{macrospNets}
@@
 \usepackage{listings}
+
 \lstset{basicstyle=\small}
@@
 
-\title{Using SMT engine to generate Symbolic Automata\thanks{This work was partially 
-funded by the Associated Team FM4CPS
-  between INRIA and ECNU, Shanghai}}
-\author{ Xudong Qin\inst{1,2}  \ \ \  Simon Bliudze\inst{3} \ \ \ Eric Madelaine\inst{1}
-  \ \ \  Min Zhang\inst{2}} 
-\institute{Universit\'e C\^ote d'Azur, Inria, CNRS, I3S, 06902 Sophia Antipolis, France
-        \and Shanghai Key Laboratory of Trustworthy Computing, ECNU, China
-\and INRIA Lille -- Nord Europe, 40 avenue Halley,
-59650 Villeneuve d'Ascq,
-France}
+% Volume frontmatter
+% ==================
+\input{eceasst/frontmatter}
+
+\title{Using an SMT engine to generate Symbolic Automata}
+\author{ Xudong Qin\autref{1}\sponsor{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai},
+  Simon Bliudze\autref{2}, Eric Madelaine\autref{3}, and Min Zhang\autref{4}} 
+\institute{\autlabel{1} \email{marsxd@gmail.com}\\
+  \autlabel{4} \email{mzhang@sei.ecnu.edu.cn}\\
+  Shanghai Key Laboratory of Trustworthy Computing, ECNU, China\par
+  \autlabel{2} \email{simon.bliudze@inria.fr}\\
+  INRIA Lille -- Nord Europe, 40 avenue Halley, 59650 Villeneuve d'Ascq,
+France\par
+  \autlabel{3} \email{eric.madelaine@inria.fr}\\
+  Universit\'e C\^ote d'Azur, Inria, CNRS, I3S, 06902 Sophia Antipolis, France
+}
 \date{}                                           % Activate to display a given date or no date
@@
                           % Activate to display a given date or no date
-
-\begin{document}
-
-\maketitle
 
@@
 
-\begin{abstract}
-Open pNets are used to model the behaviour of open systems, both
+\abstract{Open pNets are used to model the behaviour of open systems, both
 synchronous or asynchronous, expressed in various calculi or
@@
 unsatisfiable transitions.
-As an industrial oriented use-case, we use so-called "architectures"
+As an industrial oriented use-case, we use so-called ``architectures''
 for BIP systems, that have been used in the framework of an ESA project and to specify the control software of
@@
 behavioural properties; we give 2 examples, a safety and a liveness
-property.
-\end{abstract}
+property.}
+\keywords{Networks of Synchronised Automata, Symbolic Behavioral Semantics, Compositional Analysis of Software Components, SMT}
+
+\begin{document}
+
+\maketitle
 
@@
 The open pNet model addresses this problem, using
-"holes" as process parameters, representing \emph{unspecified} subsystems.
+``holes'' as process parameters, representing \emph{unspecified} subsystems.
 The pNet model was developed in a series of
@@
 open systems encoded as pNets. The equivalence between pNets is
-"FH-bisimulation" \cite{henrio:Forte2016}, a dedicated version of
+``FH-bisimulation'' \cite{henrio:Forte2016}, a dedicated version of
 symbolic bisimulation taking the  
@@
 
-In \cite{henrio:Forte2016} we also
-proved that a pNet with finitely many pLTSs, holes, and
-synchronisation vectors, and with finite pLTSs, has a finite
-semantics. Remark that all the elements of such pNets and open automata being
+In \cite{henrio:Forte2016} we also proved:
+\begin{theorem}[Finiteness]
+  \label{Th:finiteness}
+  Given an open pNet $pnet=\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $l_i^{i\in I}$ and holes $h_j^{j\in
+  J}$, if the sets $I$ and $J$ are finite, if the synchronisation vectors of all pNets 
+  included in  $pnet$   are finite, and if
+$\forall i \in L.\, finite{(states(l_i))} \text{ and } l_i$
+has a finite number of state variables, then its semantics is an open automaton 
+$\mathcal{T}$ with finitely many states and transitions.
+\end{theorem}
+  Remark that all the elements of such pNets and open automata being
 symbolic, they can represent many classes of unbounded systems.
@@
 semantics, the interaction with the Z3 SMT solver, and we show the
-result on our  example.
+result on our example. Under the hypotheses of Theorem \ref{Th:finiteness}
+this algorithm terminates.
 
@@
 %%   in the sat check !}
-Algorithm~\ref{alg1} starts with an open pNet, and builds its set of open
-transitions. Its main loop is a classical residual algorithm: starting
-from the initial global state, it picks a state in an unexplored set, and
-computes all possible OTs, adding their target states in the
-unexplored set, until this set is empty. As the set of
-global states is finite (under the conditions above), this terminates.
 
@@
 
+Algorithm~\ref{alg1} starts with an open pNet, and builds its set of open
+transitions. Its main loop is a classical residual algorithm: starting
+from the initial global state, it picks a state in an unexplored set, and
+computes all possible OTs, adding their target states in the
+unexplored set, until this set is empty.
+%By construction, due to the
+%satisfiability test in line 6, it only produces the set of states reachable
+%through a sequence of satisfiable open transitions.
+
 The inside loop (\emph{MakeTransitions} method) applies recursively
@@
 predicate to be checked, encoded as a set of assertions.
-Here we display also the diagnosis (``sat'' or ``unsat'') generated by Z3;
+Here the behavior of the hole ``B'' appears as a variable
+``|hb\_B:13:1|'', and line 10 shows the constraint that matching with
+a synchronisation vector has imposed on the behavior of ``B''.
+Here we display also the diagnosis (``sat'' or ``unsat'') generated by Z3.
+
+\begin{figure}[t]
+  %  \centerline{\includegraphics[width=12cm]{XFIG/SMTLIB2}}
+    \centerline{\includegraphics[width=\linewidth]{XFIG/SMTLIB3}}
+  \caption{The input of the Z3 solver in SMT-LIB language and the output result}  \label{schema:smt-lib}
+\end{figure}
+
+By lack of space, we have only shown here a use-case with boolean data
+parameters, so we only require the basic SAT capability of the Z3
+engine. It should be clear that more involved examples will require
+reasonning on predicates of various data types. Z3 provides theories for reasonning
+on integers, bitstrings, enumerated types, arrays, etc.
+We also need to deal with some universal quantification on free
+variables occuring in the guards of synch vectors.
+For other data structures usual in such models, like records, or
+recursive structures, the user will have to develop its own theories.
+Decidability of these theories will condition the completeness of the
+satisfiability check, and the decidability of model-checking or
+bisimulation checking.
+
 %% \noteSB{I am not sure I understand the entire message of this phrase}\hl{though in practice our tool only needs the brute information ``sat''
@@
 % as appears in the ``unsat'' proof generated by Z3 in which ``\{= ?x66 ?x70\}'' is shown to be false (see Fig. \ref{schema:smt-lib})
-
-\begin{figure}[t]
-  %  \centerline{\includegraphics[width=12cm]{XFIG/SMTLIB2}}
-    \centerline{\includegraphics[width=\linewidth]{XFIG/SMTLIB3}}
-  \caption{The input of the Z3 solver in SMT-LIB language and the output result}  \label{schema:smt-lib}
-\end{figure}
 
@@
 %\newpage
-%\appendix
-%\section{Appendix}
+\appendix
+\section{Changes from pre-proceedings version}
+All minor requests from reviewers (typo, grammar) were already corrected in the preproceedings version.
+
+Request from Reviewer 3, that we had not done in the preproceedings, for matter of space, have now been shortly answered.
+More precisely,
+\begin{itemize}
+\item{} in section \ref{section:op-semantics}, we have added a precise statement of our finiteness theorem, that answers the question about termination of the algorithm.
+\item{-} in section \ref{section:pruning} we have added more explanations about the way that various data types theories will be handled by the SMT engine
+\end{itemize}
+
 The following appendices are included for the convenience of reviewers.
@@
 \begin{theorem}[Finiteness of open-automata.]\\
-Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
+Given an open pNet $pnet=\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $l_i^{i\in L}$ and holes $h_j^{j\in
   J}$, if the sets $L$ and $J$ are finite, if the synchronization vectors of all pNets 
-  included in  $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ 
+  included in  $pnet$ 
   are finite, and if
-$\forall i \in L.\, finite{(states(pLTS_i))} \text{ and } pLTS_i$
+$\forall i \in L.\, finite{(states(l_i))} \text{ and } l_i$
 has a finite number of state variables, then Algorithm 1 terminates

### 2019-03-04 2017-Xudong-SMT/ActaInformatica.tex
Initial , with TODO marks

--- 2019-03-04 2017-Xudong-SMT/AVOCS-2018-postproc.tex
@@
 \author{ Xudong Qin\autref{1}\sponsor{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai},
-  Simon Bliudze\autref{2}, Eric Madelaine\autref{3}, and Min Zhang\autref{4}} 
+  Simon Bliudze\autref{2}, Eric Madelaine\autref{3}, Zechen Hou\autref{1}, Yuxin Deng\autref{1}, and Min Zhang\autref{4}\todoMargin{Should we remove Min ?}} 
 \institute{\autlabel{1} \email{marsxd@gmail.com}\\
@@
 behavioural properties; we give 2 examples, a safety and a liveness
-property.}
+property.
+\todoMargin{Add new contrib}}
 \keywords{Networks of Synchronised Automata, Symbolic Behavioral Semantics, Compositional Analysis of Software Components, SMT}
@@
     generated by the algorithm.
-\item We show the interest of this approach on an
+    \item \ERIC{we define a strategy checking satisfiability of open transitions in the course the residual algorithm, and show that this ensures that we still generate the reachable part of the open automaton, and that what is generated is minimal with respect to the decidability of predicate decidability}
+\item We show the interest of this approach \ERIC{on various use-cases from different settings}, including an
     industry-inspired case-study, namely one architectural pattern
@@
 
+\TODO{use a simpler running example (e.g. Lotos Enable operator ?), and move the BIP example to a dedicated section at the end}
+
 As a running example we use the Failure Monitor architecture from the
@@
 The final open automaton includes all satisfiable OTs, and the set of
-reachable global states.
+reachable global states.  \TODO{Make this more precise : sat and reachability is computed only at the end...}
+
+\subsection{Computing reachable state space on the fly}
+\TODO{add a high level description of the new strategy, discuss decidability/approximation of the SAT checking, express some ``minimality'' property}
 
@@
 the translation () is then decoded.
+
+\section{Use-cases}
+\TODO{new section here, showing various features on different examples.
+Possible: Enable operator in Lotos, with (equivalent) state-based and data-based encodings; Associativity of Enable; simple communication protocol, specification and implementation; BIP FailureTimer architecture, including non-trivial ``Interval'' data-type and operators; without and with encoding of maximal progress.}
 

### 2019-03-05 2017-Xudong-SMT/ActaInformatica.tex
Added macros and figures for the extended FailureTimer exemple

@@
 %%\usepackage{hyperref}
+
+\input{XFIG/macros.tex}         % Definitions of macros used in XFig figures
 \usepackage{macrospNets}
-
-\input{XFIG/macros.tex}         % Definitions of macros used in XFig figures
 
@@
 \newcommand{\resp}[1][\ ]{resp.#1}
+\newcommand{\addspace}[1]{#1 }
+\newcommand{\nopri}[1][]{\ensuremath{\mathit{enc}%
+    \ifx#1\relax\else(#1)\fi}}
+\newcommand{\maxprog}[1][]{\ensuremath{\mathit{enc}_\mu%
+    \ifx#1\relax\else(#1)\fi}}
 
@@
 	\label{def:OpenTransitions}
-	An \emph{open transition} $OT$ over a set  $\langle S_i,s_{0 i}, \rightarrow_i\rangle^{i\in
-	I}$ of LTSs, a
-	set $J$ of holes, %with sorts $Sort_j^{j\in J}$
+	An \emph{open transition} $OT$ over
+        % a set  $\langle S_i,s_{0 i}, \rightarrow_i\rangle^{i\in I}$ of LTSs,
+        a set $J$ of holes, %with sorts $Sort_j^{j\in J}$
         and a set of states $\mathcal{S}$ is a structure of the form:	
@@
 	\inferrule*[myfraction=\reddottedrule]
-	{\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
-		\{\xrightarrow{b_j}_j\}^{j\in J}, \Pred\,, \Post}
+	{%\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
+		\{\xrightarrow{\beta_j}_j\}^{j\in J}, \Pred\,, \Post}
 	{s \xrightarrow {\alpha}s'}\,,
 	\end{mathpar}
-	where $s, s'\in\mathcal{S}$, the $a_i, b_j, \alpha$ are
-        action expressions, $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is
-        a transition of the 
-	LTS $\langle S_i,s_{0 i}, \rightarrow_i\rangle$, $b_j$
+	where $s, s'\in\mathcal{S}$, the $a_i, \beta_j, \alpha$ are
+        action expressions,
+        % $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the 
+	% LTS $\langle S_i,s_{0 i}, \rightarrow_i\rangle$
+        $\beta_j$
         is an action of the hole $j$, and $\alpha$ is the resulting action
@@
 	over the variables of the terms, labels, and states $s_i$,
-        $b_j$, $s$, $\alpha$. \Post\ is a set of equations that  
+        $\beta_j$, $s$, $\alpha$. \Post\ is a set of equations that  
 	hold \emph{after the open transition}, represented as a
@@
 	An \emph{open automaton} is a structure\\ $A =
-	\langle \mathit{LTS}_i^{i\in I},J,\mathcal{S},s_0,\mathcal{T}\rangle$ where:
+	\langle J,\mathcal{S},s_0,\mathcal{T}\rangle$ where:
 	\begin{itemize}
 		\item[$\bullet$]  $I$ and $J$ are  sets of indices,
-		\item[$\bullet$]  $LTS_i^{i\in I}$ is a family of LTSs,
+	%	\item[$\bullet$]  $LTS_i^{i\in I}$ is a family of LTSs,
 		\item[$\bullet$]  $\mathcal{S}$ is a set of states and $s_0 \in \mathcal{S}$ the initial state,
@@
 		$t\in \mathcal{T}$, there exist $I'$, $J'$ with $I'\subseteq I$, $J'
-		\subseteq J$, such that $t$ is an open transition over $LTS_i^{i\in I'}$, $J'$,
+		\subseteq J$, such that $t$ is an open transition over $J'$,
 		and  $\mathcal{S}$.
@@
 \label{section:resultOA}
-
+\noteEM{This is the original example from the Avocs paper}
 For this example, the tool builds 184 open transitions, whereof 173
@@
 %%   one involving the timer data (number of ticks ?)}
+
+\subsection{Extended version of the FailureTimer BIP Architecture}
+\label{section:resultTimerInterval}
+\noteEM{Here we have extended the FailureTimer architecture using time intervals,
+  that makes more interesting the timeout/reset temporal behavior}
+
+We present here an extended version of the FailureTimer BIP
+architecture, in which the timeout action can occur
+non-deterministicaly during some time interval. This behavior is more
+realistic, but ensuring safety is a bit more complicated, as it
+involves reasonning on the time intervals in the predicates of the
+open automaton.
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=0.9\columnwidth]{XFIG/BIPspec-ArchFailureTimerMax-v4}
+  \caption{The BIP specification of the Failure Monitor architecture}
+  \label{fig:schema:ArchFailure:BIP}
+\end{figure}
+
+\ref{fig:schema:ArchFailure:BIP} shows components
+$\NameTimer$(imer) and $\NameCtrl$(ontrol), with interfaces
+$\btuple{
+  \{t, z\},
+  \{\PortTick, \PortCancel, \PortTOT\},
+  \bigl\{\!\PortTick \mapsto \{t, z\}\!\bigr\}
+}$,
+and
+$\btuple{
+  \{\mathit{zone}\},
+  \{\PortReset, \PortFail, \PortResume, \PortTOC\},
+  \bigl\{\!\PortFail \mapsto \{\mathit{zone}\}\!\bigr\}
+}$
+respectively.
+Variable $t$ is implicitly assumed to be an integer.  Variables $z$
+and $\mathit{zone}$ are  integer intervals of
+the form $[l,u]$.
+
+\TODO{refer to Research Report (not yet avaialble) or add an appendix,
+  for a full explanation of this example, 
+  and the translation from BIP to pNets}
+
+\ref{fig:FailureTimer:pNet} shows the encoding of the Failure Monitor
+architecture, including the encodings of the two coordinators, \ie
+$\nopri[\NameTimer]$ and $\nopri[\NameCtrl]$.  Notice that the
+encoding in the figure is slightly optimised: some of the ports do not
+have an associated Boolean value, nor the additional loop transitions.
+We will explain this optimisation after we define the
+encoding of the interaction model.
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=0.9\columnwidth]{XFIG/FailureTimerPNET-v4}
+  \caption{The open pNet encoding the Failure Monitor architecture (\ref{fig:schema:ArchFailure:BIP}) without the Max Progress priority model}
+  \label{fig:FailureTimer:pNet}
+  \end{figure}
 

### 2019-03-05 2017-Xudong-SMT/ActaInformatica.tex
added OA for Failure Timer

@@
 
-\ref{fig:schema:ArchFailure:BIP} shows components
+Figure \ref{fig:schema:ArchFailure:BIP} shows components
 $\NameTimer$(imer) and $\NameCtrl$(ontrol), with interfaces
@@
 
-\ref{fig:FailureTimer:pNet} shows the encoding of the Failure Monitor
+The safety
+property \emph{``There is always a possibility to reset the system
+  after a single failure''} (\ie without
+  additional failures having to occur in the meantime) enforced by the
+  Failure Monitor architecture can be specified using CTL as
+    $\AG
+\bigl(\PortFail \rightarrow \EX \EU[]{\lnot \PortFail}{
+  \PortReset}\bigr)$.  Additional properties are provided in \ref{RR}.
+
+Figure \ref{fig:FailureTimer:pNet} shows the encoding of the Failure Monitor
 architecture, including the encodings of the two coordinators, \ie
-$\nopri[\NameTimer]$ and $\nopri[\NameCtrl]$.  Notice that the
-encoding in the figure is slightly optimised: some of the ports do not
-have an associated Boolean value, nor the additional loop transitions.
-We will explain this optimisation after we define the
-encoding of the interaction model.
+$\nopri[\NameTimer]$ and $\nopri[\NameCtrl]$.
 
@@
 \end{figure}
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=0.9\columnwidth]{TimerOADetailed}
+  \caption{The open Automaton of the Failure Monitor Architecture}
+  \label{fig:ArchFailure:OA}
+\end{figure}
+
+Figure \ref{fig:ArchFailure:OA} shows the open automaton built by our
+algorithm. For reasons of readability, we did not show the full
+details of the open transitions on this figure. Below we list the
+first 3 of them (full details available in \ref{RR}). 
+This automaton has 12 transitions, including those encoding various
+possible firing of some interactions (e.g. OT 2 and 3 for
+{\PortFail}). It looks like the rough behaviour is
+reasonable, although a detailed study shows that the property stated
+above does not hold, because of the
+{\PortFail} loops on states $11$ and $12$. This is because we did not
+use the maximal progress assumption here. If we do, we get the
+corrected behaviour in \fig{ArchFailure:OA-MaxProgress}
+(\app{full-results}), in which $OT_7$ has disappeared, and $OT_2$ and
+$OT_{10}$ have been restricted to $b0=\false$.
+
+  \begin{figure}[t]
+  \centering
+  \includegraphics[width=\columnwidth]{TimerOAMaxProgress}
+  \caption{The open Automaton of the Failure Monitor Architecture,
+    with Maximal Progress}
+  \label{fig:ArchFailure:OA-MaxProgress}
+  \end{figure}
+
+  \TODO{Eric: Explain}
 

### 2019-03-05 2017-Xudong-SMT/ActaInformatica.tex
added soem details in use-case

@@
 
+%% CTL
+\newcommand{\AG}[1][\ ]{\ensuremath{\mathtt{AG}#1}}
+\newcommand{\AF}[1][\ ]{\ensuremath{\mathtt{AF}#1}}
+\newcommand{\EF}[1][\ ]{\ensuremath{\mathtt{EF}#1}}
+\newcommand{\EX}[1][\ ]{\ensuremath{\mathtt{EX}#1}}
+\newcommand{\AW}[3][\ ]{\ensuremath{\mathtt{A}\left[#2\ \mathtt{W}\ #3\right]#1}}
+\newcommand{\EU}[3][\ ]{\ensuremath{\mathtt{E}\left[#2\ \mathtt{U}\ #3\right]#1}}
+
 \makeatother
@@
   \centering
-  \includegraphics[width=0.9\columnwidth]{TimerOADetailed}
+  \includegraphics[width=0.9\columnwidth]{XFIG/TimerOADetailed}
   \caption{The open Automaton of the Failure Monitor Architecture}
@@
 use the maximal progress assumption here. If we do, we get the
-corrected behaviour in \fig{ArchFailure:OA-MaxProgress}
-(\app{full-results}), in which $OT_7$ has disappeared, and $OT_2$ and
+corrected behaviour in Figure \ref{fig:ArchFailure:OA-MaxProgress}, in
+which $OT_7$ has disappeared, and $OT_2$ and 
 $OT_{10}$ have been restricted to $b0=\false$.
+
+\bigskip
+\noindent
+$  OT_1  = \openrule
+{\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
+{\ostate{00} \OTarrow{init} \ostate{11}}
+$
+
+\medskip    
+\noindent
+$  OT_2  = \openrule
+{\{B\mapsto fail(b0)\},\\
+  t<GetMax(z) \land b1=false \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),\\
+  \{z:=z1\} }
+{\ostate{11} \OTarrow{fail} \ostate{11}}
+$
+\medskip
+
+\noindent
+  $  OT_3  = \openrule
+  {\{B\mapsto fail(b0)\},\\
+    t<GetMax(z) \land b1=true \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),\\
+    \{z:=z1\} }
+  {\ostate{11} \OTarrow{fail} \ostate{12}}
+  $
+  \medskip
 
@@
   \centering
-  \includegraphics[width=\columnwidth]{TimerOAMaxProgress}
+  \includegraphics[width=\columnwidth]{XFIG/TimerOAMaxProgress}
   \caption{The open Automaton of the Failure Monitor Architecture,
@@
   \TODO{Eric: Explain}
+\begin{itemize}
+\item $OT_2$ and $OT_{10}$ have changed because $b0=true$ is no longer possible
+\item $OT_7$ has disappeared because it is now unsat.
+\end{itemize}
 

### 2019-03-06 2017-Xudong-SMT/ActaInformatica.tex
more todos, and added proof of Th1

@@
 
+\TODO{the proof of the finiteness theorem refers to SOS rules Tr1 and
+  Tr2. So maybe we must include (and explain) these here. One problem
+  is that these rules have been modified/improved with each new
+  publication of pNets papers, so we have to decide which version we
+  use here}
+
 In \cite{henrio:Forte2016} we also proved:
@@
 symbolic, they can represent many classes of unbounded systems.
+
+\begin{proof}
+  \noteEM{I tentatively copied the proof here, from RR-8898. We should
+    check if it is sufficient with this version of the algorithm, or
+    if it can be make more precise (some added analysis of the
+    behavior of matching/combining/filetring ?)}
+  The possible set of states of the open-automaton is the cartesian
+  product of the states of its leaves $pLTS_i^{i\in L}$, that is finite by
+  hypothesis. So the top-level residual loop of Algorithm 1 terminates provided each 
+  iteration terminates. The enumeration of open-transitions in step 2b is bounded by the
+  number of applications of rules Tr2 on the structure of the
+  pNet tree, with a finite number of synchronisation vectors applying
+  at each node the number of global open transition is finite. Similarily rule Tr1 is 
+  applied finitely if the number
+  of transitions of each pLTS is finite. So we get finitely many deduction trees, and
+  open-transitions which ensures that each internal loop of Algorithm 1 terminates.
+  \end{proof}
 
@@
 
-\subsection{Computing reachable state space on the fly}
-\TODO{add a high level description of the new strategy, discuss decidability/approximation of the SAT checking, express some ``minimality'' property}
-
 %
@@
 In order to avoid such mistakes,
+\TODO{these assignment sets collect potential assignments from all OTs
+  in the generated automaton. If we minimize the generated state
+  space, we will get less assignements, and potentialy also get better
+  minimization... }
 
@@
 the solver can use specific properties of each action algebra.
+
+\subsection{Computing reachable state space on the fly}
+\TODO{add a high level description of the new strategy, discuss decidability/approximation of the SAT checking, express some ``minimality'' property}
 
@@
 \bigl(\PortFail \rightarrow \EX \EU[]{\lnot \PortFail}{
-  \PortReset}\bigr)$.  Additional properties are provided in \ref{RR}.
+  \PortReset}\bigr)$.  Additional properties are provided in \ref{TimerRR}.
 
@@
 details of the open transitions on this figure. Below we list the
-first 3 of them (full details available in \ref{RR}). 
+first 3 of them (full details available in \ref{TimerRR}). 
 This automaton has 12 transitions, including those encoding various

### 2019-03-07 2017-Xudong-SMT/ActaInformatica.tex
Acta Informatica style

@@
 
-\documentclass{eceasst}
+\documentclass[actinf,draft]{svjour}
+%\documentclass[draft]{svjour3}
 \usepackage{etex}
@@
 \usepackage{array,booktabs}
-\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
+%\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
 %\usepackage{epsfig,color,enumitem}
 \usepackage{epsfig,enumitem}
-\usepackage[%
-    font={small,sf},
-    labelfont=bf,
-    format=hang,    
-    format=plain,
-    margin=0pt,
-    %% width=0.8\textwidth,
-    aboveskip=4pt,
-    belowskip=-18pt,
-]{caption}
-\usepackage[list=true]{subcaption}
+%% \usepackage[%
+%%     font={small,sf},
+%%     labelfont=bf,
+%%     format=hang,    
+%%     format=plain,
+%%     margin=0pt,
+%%     %% width=0.8\textwidth,
+%%     aboveskip=4pt,
+%%     belowskip=-18pt,
+%% ]{caption}
+%% \usepackage[list=true]{subcaption}
 
@@
 % ==================
-\input{eceasst/frontmatter}
+% \input{eceasst/frontmatter}
 
 \title{Using an SMT engine to generate Symbolic Automata}
-\author{ Xudong Qin\autref{1}\sponsor{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai},
-  Simon Bliudze\autref{2}, Eric Madelaine\autref{3}, Zechen Hou\autref{1}, Yuxin Deng\autref{1}, and Min Zhang\autref{4}\todoMargin{Should we remove Min ?}} 
-\institute{\autlabel{1} \email{marsxd@gmail.com}\\
-  \autlabel{4} \email{mzhang@sei.ecnu.edu.cn}\\
-  Shanghai Key Laboratory of Trustworthy Computing, ECNU, China\par
-  \autlabel{2} \email{simon.bliudze@inria.fr}\\
-  INRIA Lille -- Nord Europe, 40 avenue Halley, 59650 Villeneuve d'Ascq,
-France\par
-  \autlabel{3} \email{eric.madelaine@inria.fr}\\
-  Universit\'e C\^ote d'Azur, Inria, CNRS, I3S, 06902 Sophia Antipolis, France
-}
-\date{}                                           % Activate to display a given date or no date
+\author{ Xudong Qin\inst{1},
+  Simon Bliudze\inst{2} \and Eric Madelaine\inst{3} \and Zechen
+  Hou\inst{1} \and Yuxin Deng\inst{1} \and Min Zhang\inst{4}}%\todoMargin{Should we remove Min ?}} 
+%% \institute{\autlabel{1} \email{marsxd@gmail.com}\\
+%%   \autlabel{4} \email{mzhang@sei.ecnu.edu.cn}\\
+%%   Shanghai Key Laboratory of Trustworthy Computing, ECNU, China\par
+%%   \autlabel{2} \email{simon.bliudze@inria.fr}\\
+%%   INRIA Lille -- Nord Europe, 40 avenue Halley, 59650 Villeneuve d'Ascq,
+%% France\par
+%%   \autlabel{3} \email{eric.madelaine@inria.fr}\\
+%%   Universit\'e C\^ote d'Azur, Inria, CNRS, I3S, 06902 Sophia Antipolis, France
+%% }
+\institute{Shanghai Key Laboratory of Trustworthy Computing, ECNU,
+  China, \email{marsxd@gmail.com, zechen@sei.ecnu.edu.cn,
+  yxdeng@sei.ecnu.edu.cn, mzhang@sei.ecnu.edu.cn}
+  \and INRIA Lille -- Nord Europe, 40 avenue Halley, 59650 Villeneuve
+  d'Ascq, \email{simon.bliudze@inria.fr}
+  \and Universit\'e C\^ote d'Azur, Inria, CNRS, I3S, 06902 Sophia
+  Antipolis, France, \email{eric.madelaine@inria.fr}}
+
+% \date{}                                           % Activate to display a given date or no date
 
                           % Activate to display a given date or no date
+
+\begin{document}
+
+\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}
+\maketitle
 
@@
 property.
-\todoMargin{Add new contrib}}
+\TODO{Add new contrib}
 \keywords{Networks of Synchronised Automata, Symbolic Behavioral Semantics, Compositional Analysis of Software Components, SMT}
-
-\begin{document}
-
-\maketitle
+}
 
@@
     generated by the algorithm.
-    \item \ERIC{we define a strategy checking satisfiability of open transitions in the course the residual algorithm, and show that this ensures that we still generate the reachable part of the open automaton, and that what is generated is minimal with respect to the decidability of predicate decidability}
+    \item \ERIC{we define a strategy checking satisfiability of open transitions in the course the residual algorithm, and show that this ensures that we still generate the reachable part of the open automaton, and that what is generated is minimal with respect to the decidability of predicate satisfiability}
 \item We show the interest of this approach \ERIC{on various use-cases from different settings}, including an
@@
 \begin{proof}
-  \noteEM{I tentatively copied the proof here, from RR-8898. We should
+  \TODO{I tentatively copied the proof here, from RR-8898. We should
     check if it is sufficient with this version of the algorithm, or
@@
 \label{section:resultOA}
-\noteEM{This is the original example from the Avocs paper}
+\TODO{This is the original example from the Avocs paper}
 For this example, the tool builds 184 open transitions, whereof 173
@@
 \label{section:resultTimerInterval}
-\noteEM{Here we have extended the FailureTimer architecture using time intervals,
+\TODO{Here we have extended the FailureTimer architecture using time intervals,
   that makes more interesting the timeout/reset temporal behavior}

### 2019-03-07 2017-Xudong-SMT/ActaInformatica.tex
draft of smart algo

@@
 \begin{algorithmic}[1]
-\Require A pNet $P$ (cannot be a hole)
+\Require A pNet $P$ (can be a pLTS, but not a hole)
         %\qquad \hl{\textbackslash\textbackslash~SB: was `` pn ''}
@@
 	\State $\mathit{OTs} = \mathit{MakeTransitions}(P, S)$;
-%%        \State Store $\mathit{OT}$ in $L$; 
 	\For {each $\mathit{OT} \in \mathit{OTs}$}
-        Check satisfiability of $\mathit{OT}$ using the SMT solver;
-        \IfThen {$SAT(\mathit{OT})$}
-                {\State \{Add $\mathit{OT}$ to $L$;
-                  \State Let $S'$ be the target global state of $\mathit{OT}$
+          \State Add $\mathit{OT}$ to $L$;
+          \State Let $S'$ be the target state of $\mathit{OT}$
+          Add $S'$ to the unexplored states if necessary:
 	  \IfThen{($S' \not\in U \cup E$)}{Add $S'$ into $U$;}
-                  \}}
 	  \EndFor
 \EndWhile
-%%\State Prune the unsatisfiable open transitions in $L$ using the SMT solver;
+\State \ERIC{Prune the unsatisfiable open transitions in $L$ using the SMT
+solver; only keep reachable global states;}
 \State \Return $\mathit{OA}=(\mathit{InitState}(P),L)$;
@@
 unexplored set, until this set is empty.
+
+\ERIC{Before the SAT checking step, it may contain symbolic transitions that
+do not have valid ground instanciations. This is not logicaly
+incorrect, but is naturaly not an optimal representation. So we prune
+these UNSAT transitions: at the root of the pNet, the predicate of each OT is translated
+into SMTlib assertions, and checked for satisfiability.
+The final open automaton includes all satisfiable OTs, and the set of
+reachable global states.}
 %By construction, due to the
@@
 holes of the node, so \emph{MakeTransitions} is never called on a hole.
-
-At the root of the pNet, the predicate of each OT is translated
-into SMTlib assertions, and checked for satisfiability.
-%
-The final open automaton includes all satisfiable OTs, and the set of
-reachable global states.  \TODO{Make this more precise : sat and reachability is computed only at the end...}
-
-%
-%% Unsatisfiable
-%% OTs are pruned, and the final open automaton is computed as the set of
-%% global states reachable by satisfiable OTs.
 
@@
 \subsection{Computing reachable state space on the fly}
-\TODO{add a high level description of the new strategy, discuss decidability/approximation of the SAT checking, express some ``minimality'' property}
+\TODO{add a high level description of the new strategy, discuss
+  decidability/approximation of the SAT checking, express some
+  ``minimality'' property}
+
+The basic algorithm from the previous section potentialy explores some
+areas of the global state-space that will not be reachable after
+checking the OTs' predicates for satisfiability. Incorporating the
+satisfiability check inside the residual algorithm will definitely
+save some of these useless computation. More precisely, it will still
+create, and submit to Z3, the OTs at the ``border'' of the state-space, but
+not the transitions issued from non-reachable global states.
+
+\ERIC{But there is more to this. As mentionned above, we collect all
+possible (symbolic) assignments of state variables, in the
+computed open automaton. By avoiding building the OTs coming from
+unreachable states, we also avoid adding the corresponding assignments
+to the variables of their target states. The set of possible
+assignments is an over approximation of possible values of the
+variables of such state, so narrowing it means we get a better
+approximation, and potentialy more informations, that can be used to
+the SAT check of subsequent transitions.}
+\TODO{Beware, I think this is dangerous... Xudong, do we really use
+  assignment information in SAT checking ? In the ``smart'' version, I
+  think we must NOT use it, because we do not yet have collected all
+  possible assignments.}
+
+Algorithm~\ref{alg3} implement this new stategy: ...
+
+\begin{algorithm}[h]
+  \caption{``Smart'' Reachable Open Automaton Generation}
+  \label{alg3}
+\begin{algorithmic}[1]
+\Require A pNet $P$ (cannot be a hole)
+        %\qquad \hl{\textbackslash\textbackslash~SB: was `` pn ''}
+\State Initialize sets $U=\{\mathit{InitState}(P)\}$ and $E=\emptyset$,
+for unexplored and explored global states, respectively; $L=\emptyset$ for the resulting OTs;
+\While{!$\mathit{isEmpty}(U)$}
+	\State Choose $S$ in $U$; remove $S$ from $U$, add $S$ to $E$;
+        %\qquad \hl{\textbackslash\textbackslash~SB: was `` Choose $S$ in $U$ ''}
+	\State $\mathit{OTs} = \mathit{MakeTransitions}(P, S)$;
+%%        \State Store $\mathit{OT}$ in $L$; 
+	\For {each $\mathit{OT} \in \mathit{OTs}$}
+        Check satisfiability of $\mathit{OT}$ using the SMT solver;
+        \IfThen {$SAT(\mathit{OT})$}
+                {\State \{Add $\mathit{OT}$ to $L$;
+                  \State Let $S'$ be the target global state of $\mathit{OT}$
+	          \IfThen{($S' \not\in U \cup E$)}{Add $S'$ into $U$;}
+                  \}}
+	\EndFor
+\EndWhile
+%%\State Prune the unsatisfiable open transitions in $L$ using the SMT solver;
+\State \Return $\mathit{OA}=(\mathit{InitState}(P),L)$;
+
+\end{algorithmic}  
+\end{algorithm}
+
+\TODO{Candidate theorems:
+  - All reachable states from algorithm 1 are kept by Algorithm 3\\
+  - Algorithm 3 computes an open automaton that is minimal with
+  respect of SAT checking decidability.\\
+  Of course we have to define this notion of minimality, that may be a
+  little tricky}
 

### 2019-03-08 2017-Xudong-SMT/ActaInformatica.tex
tableau resultats

@@
 	\end{tabular}
+
 \end{table}
@@
 
-Algorithm~\ref{alg3} implement this new stategy: ...
+Algorithm~\ref{alg3} implement this new stategy: \TODO{Explain
+  significant detials}
 
@@
 \end{itemize}
+
+\subsection{Benefits from the Smart algorithm}
+
+	\begin{tabular}{p{4cm}p{3cm}p{3cm}}
+		\hline\specialrule{0em}{1pt}{1pt}
+		Use-case & Brute force & Smart algorithm
+                \\\specialrule{0em}{1pt}{1pt}
+		\hline\specialrule{0em}{3pt}{3pt}
+		Enable operator   			&
+                5 SAT OTs           &
+                5 SAT OTs
+                \\\specialrule{0em}{1pt}{1pt}
+
+                ``(P>Q)>R'' &
+                55 UNSAT           &
+                42 UNSAT
+                \\\specialrule{0em}{1pt}{1pt}
+		&
+                376 ms 				&
+                344 ms  
+		\\\hline\specialrule{0em}{3pt}{3pt}
+		SimpleProt    			&
+                7 SAT OTs           &
+                7 SAT OTs
+                \\\specialrule{0em}{1pt}{1pt}
+
+                (no holes)&
+                260 UNSAT           &
+                57 UNSAT
+                \\\specialrule{0em}{1pt}{1pt}
+		&
+                1536 ms 				&
+                359 ms  
+%                \\\specialrule{0em}{1pt}{1pt}
+%                \textsl{for any sort} & & $=,\ \ne$
+		\\\hline\specialrule{0em}{1pt}{1pt}
+		SimpleProt    			&
+                19 SAT OTs           &
+                19 SAT OTs
+                \\\specialrule{0em}{1pt}{1pt}
+
+                (with 2 client holes)&
+                836 UNSAT           &
+                185 UNSAT
+                \\\specialrule{0em}{1pt}{1pt}
+		&
+                2496 ms 				&
+                844 ms  
+		\\\hline\specialrule{0em}{1pt}{1pt}
+		FailureTimer    			&
+                12 SAT OTs           &
+                12 SAT OTs
+                \\\specialrule{0em}{1pt}{1pt}
+
+                (no Max Progress)&
+                1253 UNSAT           &
+                812 UNSAT
+                \\\specialrule{0em}{1pt}{1pt}
+		&
+                1253 ms 				&
+                812 ms
+
+		\\\hline
+	\end{tabular}
 

### 2019-03-11 2016-Weak-FH-Bisim/WeakBisim.tex
corrections
Proof lemma 6 in progress
work in progress

@@
 Note that this does not mean that any two pNets can be composed and produce an open 
-transition. Indeed, the predicate $\Pred\land\Pred\land \alpha_Q=\beta_{j_0}$ is not 
+transition. Indeed, the predicate $\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0}$ is not 
 be satisfiable if the action of $\alpha_Q$ cannot be matched with $\beta_{j_0}$.
@@
  \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred \iff \Pred\,'
-		\land \!\!\bigwedge_{p=0}^n(\alpha_p= \beta_p\land \Pred_p) \qquad\text{and~}
-\Post=\Post\,'\uplus \bigotimes_{p=0}^n
+		\land \!\!\bigwedge_{p=0}^n((\alpha_p= \beta_p\land \Pred_p)\bigotimes_{i=0}^{p-1}\Post_i) 
+\\
+\text{and~}
+\Post=\Post\,' \uplus \bigotimes_{p=0}^n
 		\Post_p  
@@
 			{\ostate{(s_{p l})^{l\in L\setminus L_Q}} \OTarrow {\tau}
-				\ostate{({s}_{(p+1) l})^{l\in L_Q}}}
+				\ostate{({s}_{(p+1) l})^{l\in L_Q\setminus L_Q}}}
 		}$~~and~~ $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}} $
@@
 				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
-				\Pred^a,  
-				\Post^a}
+				\Pred\,',  
+				\Post'}
 			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
@@
 \\
-\Pred^{a}=\big(\bigwedge_{i=0}^{m_1}
+\Pred\,'=\big(\bigwedge_{i=0}^{m_1}
 {\Pred_i^{1a}}\bigotimes_{j=0}^{i-1}\subst{{\Post_j^{1a}}}\big)
@@
 ~~\qquad\quad\big(\bigwedge_{i=0}^{m_2}{\Pred_i^{3a}}\bigotimes_{j=0}^{i-1}\subst{{\Post_j^{3a}}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}}\big)\\
-\Post^a=\bigotimes_{i=0}^{m_2}{\Post_i^{3a}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}}
+\Post'=\bigotimes_{i=0}^{m_2}{\Post_i^{3a}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}}
 $
@@
 			{
-			(\gamma'_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred^b_k}},  
+			(\gamma_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred^b_k}},  
 				{{\Post^b_k}}}
@@
 $\forall j \in  (J\cap\Holes(Q)),\,
-\displaystyle{\gamma'_{kj} }=\mybigdotcup_{i=0}^{(n_k'-1)}\!\!\vis{\beta^1_{ij}}\,\dotcup\,\vis{\set{\beta^2_j}}\,\dotcup\!\!\!\mybigdotcup_{i=(n_k'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij}}
+\displaystyle{\gamma_{kj} }=\mybigdotcup_{i=0}^{(n_k'-1)}\!\!\vis{\beta^1_{ij}}\,\dotcup\,\vis{\set{\beta^2_j}}\,\dotcup\!\!\!\mybigdotcup_{i=(n_k'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij}}
 \\
-\Pred^b_k=\Big(\!\!\!\bigwedge_{i=0}^{(n_k'-1)}\!\!
+\Pred_k=\Big(\!\!\!\bigwedge_{i=0}^{(n_k'-1)}\!\!
 {\Pred_i^{1b}}\bigotimes_{j=0}^{(i-1)}\subst{{\Post_j^{1b}}}\Big)
@@
 ~\qquad\qquad\Big(\!\!\!\bigwedge_{i=(n_k'+1)}^{(n_k-1)}\!\!\!{\Pred_i^{3b}}\bigotimes_{j=n_k'+1}^{(i-1)}\subst{{\Post_j^{3b}}}\subst{{\Post^{2b}}}\bigotimes_{i=0}^{(n_k'-1)}\subst{{\Post_i^{1b}}}\Big)\\
-\Post^b_k=\bigotimes_{i=(n_k'+1)}^{(n_k-1)}\!\!\!{\Post_i^{3b}}\Big(\subst{{\Post^{2b}}}\bigotimes_{i=0}^{(n_k'-1)}\subst{{\Post_i^{1b}}}\Big)
+\Post_k=\bigotimes_{i=(n_k'+1)}^{(n_k-1)}\!\!\!{\Post_i^{3b}}\Big(\subst{{\Post^{2b}}}\bigotimes_{i=0}^{(n_k'-1)}\subst{{\Post_i^{1b}}}\Big)
 $\\
@@
   $\Pred \iff \Pred\,'
-		\land \displaystyle{\bigwedge_{p=0}^n}(\alpha_p= \beta_{pj_0}\land \Pred_p), \text{and~}
-\Post=\Post\,'\uplus\bigotimes_{p=0}^n
-		\Post_p \quad$  \\
-------------------------------------------------------\\
+		\land \displaystyle{\bigwedge_{p=0}^n}((\alpha_p= \beta_{pj_0}\land \Pred_p)\bigotimes_{i=0}^{p-1}\Post_i),\text{and~}$\\
+$\displaystyle{\Post=\Post\,'\uplus\bigotimes_{p=0}^n
+		\Post_p}$  \\
 We have:\\
 $\Pred=\displaystyle{\bigwedge_{i=0}^{m_1}\!\big(\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land \bigwedge_{i=0}^{m_2}\!\Pred_i^3\big(\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}}\big)$\\
-By replacing ${\Pred^{1}_i}$,  $\Pred^2$, and ${\Pred^{3}_i}$ we obtain:\\
+By replacing ${\Pred^{1}_i}$,  $\Pred^2$, and ${\Pred^{3}_i}$ by their equivalent formula  we obtain:\\
 $\Pred \iff\displaystyle{\bigwedge_{i=0}^{m_1}({\Pred^{1a}_i}
@@
 ~~\qquad\qquad\qquad({\Pred^{2a}}\land {\Pred^{2b}}\land \alpha^2=\beta^2_{j_0})	\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land\\
-~~\qquad\qquad\bigwedge_{i=0}^{m_2} ({\Pred^{3a}_i}\land {\Pred^{3b}_i}\land \alpha^3_i=\beta^3_{ij_0})\big(\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\big)
-		$\\
+~~\qquad\qquad\bigwedge_{i=0}^{m_2} ({\Pred^{3a}_i}\land {\Pred^{3b}_i}\land \alpha^3_i=\beta^3_{ij_0})\big(\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\big)$\\
 By distribution of the substitution operation over the logical operator we can deduce:\\
@@
 ~~\qquad\qquad\quad\big(\bigwedge_{i=0}^{m_2}{\Pred_i^{3a}}\bigotimes_{j=0}^{i-1}\subst{{\Post_j^{3a}}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}}\big) \land\\	
-~\qquad\qquad\quad\bigwedge_{i=0}^{m_1}({\Pred^{1b}_i}\land \alpha^1_i=\beta^1_{ij_0}) \bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land({\Pred^{2b}}\land \alpha^2=\beta^2_{j_0})	\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land\\
-~\qquad\qquad\quad\bigwedge_{i=0}^{m_2} ({\Pred^{3b}_i}\land \alpha^3_i=\beta^3_{ij_0})\big(\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\big)
+~\qquad\qquad\quad\bigwedge_{i=0}^{m_1}({\Pred^{1b}_i}\land \alpha^1_i=\beta^1_{ij_0}) \bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\land({\Pred^{2b}}\land \alpha^2=\beta^2_{j_0})	\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land\\
+~\qquad\qquad\quad\bigwedge_{i=0}^{m_2} ({\Pred^{3b}_i}\land \alpha^3_i=\beta^3_{ij_0})\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}
 $\\		
 Therefore, we have:\\
-$\Pred\iff \Pred^a \wedge\\
-~~\qquad\qquad\quad\displaystyle{\big(\bigwedge_{i=0}^{m_2}{\Pred_i^{3a}}\bigotimes_{j=0}^{i-1}\subst{{\Post_j^{3a}}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}}\big) \land}\\	
-~\qquad\qquad\quad\bigwedge_{i=0}^{m_1}({\Pred^{1b}_i}\land \alpha^1_i=\beta^1_{ij_0}) \bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land({\Pred^{2b}}\land \alpha^2=\beta^2_{j_0})	\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land\\
-~\qquad\qquad\quad\bigwedge_{i=0}^{m_2} ({\Pred^{3b}_i}\land \alpha^3_i=\beta^3_{ij_0})\big(\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\big)
-$
-
-\TODO{Je n'ai pas d'idee comment simplifier le reste!}\\
-For the postcondition we have:\\
+$\Pred\iff \Pred\,' \wedge \displaystyle{\bigwedge_{p=0}^{n}}((\alpha_p= \beta_{pj_0}\land \Pred_p)\bigotimes_{i=0}^{p-1}\Post_i)$\\ where $n=m_1+m_2+1$	\\
+Concerning the postcondition we have:\\
 $\Post=\displaystyle{\bigotimes_{i=0}^{m_2}\Post^3_i\subst{\Post^2}\bigotimes_{j=0}^{m_1}\subst{\Post^1_j}}$\\
-By replacing ${\Post^{1}_i}$,  $\Post^2$, and ${\Post^{3}_i}$ we obtain:\\
+By replacing ${\Post^{1}_i}$,  $\Post^2$, and ${\Post^{3}_j}$ we obtain:\\
 $\Post= \displaystyle{\bigotimes_{i=0}^{m_2}\subst{{\Post^{3a}_i}\uplus 
@@
 		{\Post^{1b}_i}}}\\
-~~\qquad= \bigotimes_{i=0}^{m_2}{\Post_i^{3a}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}} \uplus \ldots  $
+~~\qquad= \bigotimes_{i=0}^{m_2}{\Post_i^{3a}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}} \uplus \bigotimes_{i=0}^{m_2}{\Post_i^{3b}}\subst{{\Post^{2b}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1b}}} \\
+~~\qquad= \Post' \uplus \bigotimes_{j=0}^{n} \Post_j $\\
+ where $n=m_1+m_2+1$	
 \end{proof}
-\TODO{l'autre terme a voir!}
+\TODO{Pour le post j'ai fait court, je n'ai pas developpe...?}
 
@@
 		\Post_p}
-	{\ostate{s_{p i}^{i\in L_p}} \OTWeakarrow {\alpha_p}
+	{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
 		\ostate{s_{(p+1) i}^{\, i\in L_Q}}}
@@
 \begin{mathpar}
-J_Q=\bigcup_{\begin{array}{l}
-p\in[0..n]
-\end{array}} J_{p}
-\text{\qquad and\qquad} 
-\Pred\,'=\Pred\land   \!\!\bigwedge_{p\in[0..n]}(\alpha_p=\beta_p\land \Pred_p)
+J_Q=\displaystyle{\bigcup_{p=0}^nJ_{p}}
+\qquad
+\Pred\,'=\Pred\land \bigwedge_{p=0}^{n}(\alpha_p=\beta_p\land \Pred_p)\bigotimes_{i=0}^{p-1}\Post_i
 \\
-\forall j\in J_p,\,\gamma_j= \mathop{\dot{\bigcup}}_{p\in [0..n]} \gamma_{p j} 
+\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}}\text{\quad and\quad}
 \Post\,'=\Post\uplus\bigotimes_{p=0}^{n}
@@
 		{
-			\gamma_j^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
+			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
 			\Pred\,',  \Post\,'
@@
 \end{lemma}
-\TODO{proof}
+\TODO{Proof}
+
+\begin{proof} Suppose we have:
+\begin{mathpar}
+%\[
+P\models{\openrule
+	{
+		\gamma_j^{j\in J}, 
+		\Pred,  
+		\Post}
+	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
+		\ostate{s_i'^{\, i\in L}}}
+}
+\end{mathpar}
+By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
+$ \forall i \in [0..m].\openrule
+    {
+       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
+         {s_{il}^{\, l\in L} \OTarrow {\tau} s_{(i+1)l}^{\, l\in L}} \in \mathcal{T} \quad \wedge
+\quad
+\openrule
+         {
+           \set{\beta^2},\Pred^2,\Post^2 }
+         {t_{l}^{\, l\in L} \OTarrow {\alpha} {t'}_{l}^{\,l\in L}} \in \mathcal{T}
+\quad \wedge\\
+\forall i \in [0..n].\openrule
+         {
+           \set{\beta^3_i},\Pred^3_i, \Post^3_i}
+         {v_{il}^{\, l\in L} \OTarrow {\tau} v_{(i+1)l}^{\, l\in L}} \in \mathcal{T}$ 
+\\
+where for all $l\in L$:\\
+$s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
+$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i}}}\\
+\Pred=\bigwedge_{i=0}^{m_1}\!\big(\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land \bigwedge_{i=0}^{m_2}\!\Pred_i^3\big(\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\big)\\
+\Post=\bigotimes_{i=0}^{m_2}\Post^3_i\subst{\Post^2}\bigotimes_{j=0}^{m_1}\subst{\Post^1_j}
+$\\
+
+Moreover, we have for all $p\in[0..n]$:
+
+\begin{mathpar}
+Q\models{\openrule
+	{
+		\gamma_{p j}^{j\in J_p},
+		 \Pred_p,  
+		\Post_p}
+	{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
+		\ostate{s_{(p+1) i}^{\, i\in L_Q}}}
+}		
+\end{mathpar}
+Also, by Lemma \ref{lem-rel-OT-WOT} this implies the following:\\
+$\forall k\! \in\! [0..m']\,\, Q\models{\openrule
+			{
+				(\beta^1_{kj})^{j\in J\cap\Holes(Q)}, {{\Pred_k^{1b}}},  
+				{{\Post_k^{1b}}}}
+				{\ostate{s_{kl}^{l\in L_Q}} \OTarrow {\tau}
+				\ostate{s_{(k+1)l}^{l\in L_Q}}}
+				}%\]
+,$ 
+$Q\models{\openrule
+			{
+				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred^{2b}}},  
+				{{\Post^{2b}}}}
+				{\ostate{s_{l}^{l\in L_Q}} \OTarrow {\alpha'_p}
+				\ostate{s_{l}'^{l\in L_Q}}}
+				}%\]
+$
+and
+$\forall k \in [0..n']\,\, Q\models{\openrule
+			{
+				(\beta^3_{kj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^{3b}}},  
+				{{\Post_p^{3b}}}}
+				{\ostate{s_{kl}^{l\in L_Q}} \OTarrow {\tau}
+				\ostate{s_{(k+1)l}^{l\in L_Q}}}
+				}%\]
+$\\ 
+Knowing that we have $j_0\in J$ and $\gamma_{j_0}=[\beta_0..\beta_n]$:
+
+\[ P[Q]_{j_0}  
+	\models
+	{\openrule
+		{
+			\beta_j^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
+			\Pred^2\land\Pred^{2b}\land \alpha'_p=\beta_{j_0},  
+			\Post^2\uplus \Post^{2b}}
+		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {\alpha}
+			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
+	}
+	\]
+
+Moreover, for each:
+$\openrule
+         {
+           \set{\beta_i},\Pred_i, \Post_i}
+         {s_i \OTarrow {\tau} s_{i+1}} \in \mathcal{T}$
+\qed
+\end{proof}
 

### 2019-03-11 2017-Xudong-SMT/ActaInformatica.tex

@@
 
-\documentclass[actinf,draft]{svjour}
-%\documentclass[draft]{svjour3}
+%\documentclass[actinf,draft]{svjour}
+\documentclass[smallcondensed]{svjour3}
+\smartqed  % flush right qed marks, e.g. at end of proof
+
 \usepackage{etex}
@@
 \newcommand{\coloncolon}{{:\hspace{-.2ex}:}}
+
 \makeatletter
@@
 \newcommand{\raisem@th}[3]{\raisebox{#1}{$#2#3$}}
+\makeatother
 
@@
 
-\makeatother
-
-%%\usepackage{hyperref}
-
 \input{XFIG/macros.tex}         % Definitions of macros used in XFig figures
 \usepackage{macrospNets}
+
+\usepackage{hyperref}
 
@@
 
-\title{Using an SMT engine to generate Symbolic Automata}
-\author{ Xudong Qin\inst{1},
-  Simon Bliudze\inst{2} \and Eric Madelaine\inst{3} \and Zechen
-  Hou\inst{1} \and Yuxin Deng\inst{1} \and Min Zhang\inst{4}}%\todoMargin{Should we remove Min ?}} 
-%% \institute{\autlabel{1} \email{marsxd@gmail.com}\\
-%%   \autlabel{4} \email{mzhang@sei.ecnu.edu.cn}\\
-%%   Shanghai Key Laboratory of Trustworthy Computing, ECNU, China\par
-%%   \autlabel{2} \email{simon.bliudze@inria.fr}\\
-%%   INRIA Lille -- Nord Europe, 40 avenue Halley, 59650 Villeneuve d'Ascq,
-%% France\par
-%%   \autlabel{3} \email{eric.madelaine@inria.fr}\\
-%%   Universit\'e C\^ote d'Azur, Inria, CNRS, I3S, 06902 Sophia Antipolis, France
-%% }
-\institute{Shanghai Key Laboratory of Trustworthy Computing, ECNU,
-  China, \email{marsxd@gmail.com, zechen@sei.ecnu.edu.cn,
-  yxdeng@sei.ecnu.edu.cn, mzhang@sei.ecnu.edu.cn}
-  \and INRIA Lille -- Nord Europe, 40 avenue Halley, 59650 Villeneuve
-  d'Ascq, \email{simon.bliudze@inria.fr}
-  \and Universit\'e C\^ote d'Azur, Inria, CNRS, I3S, 06902 Sophia
-  Antipolis, France, \email{eric.madelaine@inria.fr}}
-
-% \date{}                                           % Activate to display a given date or no date
-
-                          % Activate to display a given date or no date
+\newcommand{\orcid}[1]{\href{https://orcid.org/#1}{ORCID:~{#1}}}
+
+\title{Using an SMT engine to generate Symbolic Automata%
+%
+  \thanks{This work was partially funded by the Associated Team FM4CPS
+    between INRIA and ECNU, Shanghai}%
+}
+
+\author{Xudong~Qin \and
+  Simon~Bliudze \and
+  Eric~Madelaine \and
+  Zechen~Hou \and
+  Yuxin~Deng \and
+  Min~Zhang
+}
+
+\institute{Xudong Qin(\email{marsxd@gmail.com}) \and
+  Zechen Hou (\email{zechen@sei.ecnu.edu.cn}) \and
+  Yuxin Deng (\email{yxdeng@sei.ecnu.edu.cn}) \and
+  Min Zhang (\email{mzhang@sei.ecnu.edu.cn}) \at
+  Shanghai Key Laboratory of Trustworthy Computing, ECNU, China%% \\
+  %% \email{marsxd@gmail.com, zechen@sei.ecnu.edu.cn, yxdeng@sei.ecnu.edu.cn, mzhang@sei.ecnu.edu.cn}
+  \and
+  Simon Bliudze \at
+  INRIA Lille -- Nord Europe,
+  40 avenue Halley,
+  59650 Villeneuve d'Ascq,
+  France\\
+  \email{simon.bliudze@inria.fr}
+  \qquad
+  \orcid{0000-0002-7900-5271}
+  \and
+  Eric Madelaine \at
+  Universit\'e C\^ote d'Azur, Inria, CNRS, I3S, 06902 Sophia
+  Antipolis, France,\\
+  \email{eric.madelaine@inria.fr}
+}
+
+%% \author{ Xudong Qin\inst{1},
+%%   Simon Bliudze\inst{2} \and Eric Madelaine\inst{3} \and Zechen
+%%   Hou\inst{1} \and Yuxin Deng\inst{1} \and Min Zhang\inst{4}}%\todoMargin{Should we remove Min ?}} 
+%% %% \institute{\autlabel{1} \email{marsxd@gmail.com}\\
+%% %%   \autlabel{4} \email{mzhang@sei.ecnu.edu.cn}\\
+%% %%   Shanghai Key Laboratory of Trustworthy Computing, ECNU, China\par
+%% %%   \autlabel{2} \email{simon.bliudze@inria.fr}\\
+%% %%   INRIA Lille -- Nord Europe, 40 avenue Halley, 59650 Villeneuve d'Ascq,
+%% %% France\par
+%% %%   \autlabel{3} \email{eric.madelaine@inria.fr}\\
+%% %%   Universit\'e C\^ote d'Azur, Inria, CNRS, I3S, 06902 Sophia Antipolis, France
+%% %% }
+%% \institute{Shanghai Key Laboratory of Trustworthy Computing, ECNU,
+%%   China, \email{marsxd@gmail.com, zechen@sei.ecnu.edu.cn,
+%%   yxdeng@sei.ecnu.edu.cn, mzhang@sei.ecnu.edu.cn}
+%%   \and INRIA Lille -- Nord Europe, 40 avenue Halley, 59650 Villeneuve
+%%   d'Ascq, \email{simon.bliudze@inria.fr}
+%%   \and Universit\'e C\^ote d'Azur, Inria, CNRS, I3S, 06902 Sophia
+%%   Antipolis, France, \email{eric.madelaine@inria.fr}}
+
+\date{Received: date / Accepted: date}
 
 \begin{document}
-
-\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}
 \maketitle
@@
 \TODO{Add new contrib}
+\todoMargin{Should we remove Min ?}
 \keywords{Networks of Synchronised Automata, Symbolic Behavioral Semantics, Compositional Analysis of Software Components, SMT}
@@
 
-\bibliographystyle{lncs/splncs}
+\bibliographystyle{spmpsci}
 

### 2019-03-11 2016-Weak-FH-Bisim/WeakBisim.tex
skype Push

@@
 $ 
+In this equation, and using cases 1, 2 and 3 above, we have for all $k\in [0\ldots n_1+n_2+2]$, $\beta_{kj_0}=\alpha_k$.
 
@@
 
-\TODO{A revoir pas correct!: From cases 1, 2 and 3 we have for all $k\in [0\ldots n]$, $\beta_{kj_0}=\alpha_k$. Moreover,} \\
-
 We have: 
-$\displaystyle{\gamma_{j_0}}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{i{j_0}}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{i{j_0}}}=[\alpha'_0..
-\alpha'_n]$, indeed $\displaystyle{\gamma_{j_0}}$ is a a list of $\alpha_p$ such that $p\in [0..(n_1\!+\!n_2\!+\!1)] \land \alpha_p\neq \tau$.
+$\displaystyle{\gamma_{j_0}}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{i{j_0}}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{i{j_0}}}$
+
+Additionally, we have
+$[\alpha'_0..
+\alpha'_n]$ is a a list of $\alpha_p$ such that $p\in [0..(n_1\!+\!n_2\!+\!2)] \land \alpha_p\neq \tau$ where for all $k\in [0\ldots n_1+n_2+2]$, $\beta_{kj_0}=\alpha_k$.
+In other words, $\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{i{j_0}}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{i{j_0}}} = [\alpha'_0..
+\alpha'_n]$.
+This ensures that $\gamma_{j_0}=[\alpha'_0..
+\alpha'_n]$.
+
 %$\displaystyle{\gamma_{kj_0} }=\mybigdotcup_{i=0}^{(n'-1)}\!\!\vis{\beta^1_{ij_0}}\,\dotcup\,\vis{\set{\beta^2_{j_0}}}\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij_0}}$ \TODO{?????}\\
 
-For  $\gamma_{j_0}=[\beta_0..\beta_n]$ such that $\beta_i=\alpha'_i$ we have $n$ weak open transitions  $\symb{WOT}_k$ such that $k\in [0..n]$.
+Consequently, for  $\gamma_{j_0}=[\beta_0..\beta_n]$ such that $\beta_i=\alpha'_i$ we have $n$ weak open transitions  $\symb{WOT}_k$ such that $k\in [0..n]$.
 Therefore, we can conclude that we have for all $k\in [0..n]$:  
@@
 $\Post=\displaystyle{\bigotimes_{i=0}^{m_2}\Post^3_i\subst{\Post^2}\bigotimes_{j=0}^{m_1}\subst{\Post^1_j}}$\\
-By replacing ${\Post^{1}_i}$,  $\Post^2$, and ${\Post^{3}_j}$ we obtain:\\
+By replacing ${\Post^{1}_i}$,  $\Post^2$, and ${\Post^{3}_j}$ and because the ${\Post_i^{ja}}$ and ${\Post_i^{jb}}$ are independent (the ${\Post_i^{ja}}$ concern the leaves of $P$ while the ${\Post_i^{jb}}$ concern the leaves of $Q$), we obtain:\\
 $\Post= \displaystyle{\bigotimes_{i=0}^{m_2}\subst{{\Post^{3a}_i}\uplus 
@@
 \end{proof}
-\TODO{Pour le post j'ai fait court, je n'ai pas developpe...?}
 
@@
 Knowing that we have $j_0\in J$ and $\gamma_{j_0}=[\beta_0..\beta_n]$:
-
+Suppose that $Q$ moves in transition $\alpha$, then there is  a matching $p_0$ transition for some $p_0\in[0..n]$. 
 \[ P[Q]_{j_0}  
@@
 		{
-			\beta_j^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
-			\Pred^2\land\Pred^{2b}\land \alpha'_p=\beta_{j_0},  
+			(\beta^2_j)^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
+			\Pred^2\land\Pred^{2b}\land \alpha'_{p_0}=\beta^2_{j_0},  
 			\Post^2\uplus \Post^{2b}}
@@
 	\]
+NOTE: And $\beta^2_{j_0}= \beta_{p_0}$.
 

### 2019-03-11 2017-Xudong-SMT/ActaInformatica.tex

@@
 
+In each cell of the following table, we display the number of OTs whose predicates were founSAT/UNSAT by the SMT engine, and the overall time spent for the whole algorithm execution.
+
 	\begin{tabular}{p{4cm}p{3cm}p{3cm}}
@@
 		Enable operator   			&
-                5 SAT OTs           &
-                5 SAT OTs
+                5/55 OTs           &
+                5/42 OTs
                 \\\specialrule{0em}{1pt}{1pt}
@@
                 ``(P>Q)>R'' 		&
-                55 UNSAT           &
-                42 UNSAT
-                \\\specialrule{0em}{1pt}{1pt}
-		&
                 376 ms 				&
@@
 		SimpleProt    			&
-                7 SAT OTs           &
-                7 SAT OTs
+                7/260 OTs           &
+                7/57 OTs
                 \\\specialrule{0em}{1pt}{1pt}
@@
                 (no holes)&
-                260 UNSAT           &
-                57 UNSAT
-                \\\specialrule{0em}{1pt}{1pt}
-		&
                 1536 ms 				&
@@
 		SimpleProt    			&
-                19 SAT OTs           &
-                19 SAT OTs
+                19/836 OTs           &
+                19/185 OTs
                 \\\specialrule{0em}{1pt}{1pt}
@@
                 (with 2 client holes)&
-                836 UNSAT           &
-                185 UNSAT
-                \\\specialrule{0em}{1pt}{1pt}
-		&
                 2496 ms 				&
@@
 		FailureTimer    			&
-                12 SAT OTs           &
-                12 SAT OTs
+                12/235 OTs           &
+                12/180 OTs
                 \\\specialrule{0em}{1pt}{1pt}
@@
                 812 ms  
+		\\\hline\specialrule{0em}{1pt}{1pt}
+		FailureTimer X 2    			&
+                37/3136 OTs           &
+                37/2416 OTs
+                \\\specialrule{0em}{1pt}{1pt}
+
+		&
+                8923 ms 				&
+                6798 ms
 
@@
 	\end{tabular}
+
+        This shows a significant benefit of the ``smart'' strategy, in the considered use-cases, between 30 to 60\% gain depending on the examples.
 

### 2019-03-13 2017-Xudong-SMT/ActaInformatica.tex
inserted Enable example

@@
 
-In Fig.~\ref{schema:ArchFailure:pNet}, we show examples of these
+In Fig.~\ref{schema:EnableEncodings}, we show examples of these
 constructs, with two pLTSs, one hole and one pNet node encoding our running example.
 
-\section{Running example}
+\subsection{Example}
+\label{section:example}
+\TODO{Taken from \cite[Forte]}
+
+\begin{figure}[t]
+\begin{minipage}{6.1cm}
+
+  \includegraphics[width=\linewidth]{XFIG/Enable1}
+  \\[1.3ex]
+ \includegraphics[width=\linewidth]{XFIG/Enable2}
+  \caption{Two pNet encodings for  Enable }  \label{schema:enable-pnets}
+\end{minipage}
+  \hspace{2mm}
+\begin{minipage}{6cm}
+  \includegraphics[width=\linewidth]{XFIG/P-QR}
+  \caption{Composed pNet for ``P>>(Q>>R)''}  \label{schema:enable-composed}
+\end{minipage}
+
+\end{figure}
+
+	To give simple intuitions of the open pNet model and its semantics, we use
+	here a simple example based on the ``Enable'' operator of the LOTOS language.
+	In Fig. \ref{schema:enable-pnets}, we show 2 possible encodings of the  
+	``Enable'' operator.
+	In the Enable expression ``P>>Q'', an \texttt{exit(x)} statement within P
+	terminates the current process, carrying a value $x$ that
+	is captured by the \texttt{accept(x)} statement of Q.
+
+	We use a simple action algebra,
+	containing two constructors $\delta(x)$ and $acc(x)$, for any
+	possible data type of the variable $x$, corresponding to the
+	statements \texttt{exit(x)} and \texttt{accept(x)}. Both $\delta(x)$
+	and $acc(x)$ actions are
+	implicitly included in the sorts of all processes.
+	We need no specific predicate over the action expressions, apart
+	from equality of actions. 
+	In the first encoding $Enable1$, in the upper part of
+	Fig. \ref{schema:enable-pnets}, we use a controller $C_1$ with two
+	states, and simple control actions $l, r, \delta$. The second encoding
+	$Enable2$ uses a data-oriented style, with a single state controller, and a
+	state-variable $s_0$, with values in $\{0,1\}$.
+
+        In this example we use \emph{synchronised
+          actions}, to express actions that cannot be further synchronised, like the
+        $\tau$ silent action of CCS. We denote them as any action expression with the text
+        underlined, as e.g. $\underline{\delta(x_2)}$. Such
+        synchronised actions do not play any special role for defining
+        the semantics of pNets, but as one can expect, will be crucial
+        for defining weak equivalences.
+
+	Note that synchronisation vectors are defined in a parameterised
+	manner:  the first and third lines represent one vector
+	for each parameterised action in the Sort of hole $P$
+	(resp. $Q$). This notation can also use predicates, as in the first
+	case, in which we want the vector to apply to any action of $P$
+	except $\delta(z)$.
+
+	In Fig. \ref{schema:enable-composed}, we enrich our example by
+	composing 2 occurences of the Enable1 pNet. To simplify,
+	we only have represented one instance of the synchronisation vector set,
+	and of the controller.
+
+\section{Operational Semantics for Open pNets}
+\label{section:op-semantics}
+
+The semantics of open pNets will be defined as an open automaton, that
+is an automaton where each transition composes transitions 
+of several
+% \noteSB{These should all be pLTSs, right? Or did I miss
+%  something?}\noteEM{Hum, nor really, something intermediate; the actions there can be
+%  parameterised actions, but the label has no guard and no
+%  assignments}
+LTSs with the actions of some holes; the transition occurs if some predicates hold,
+and can involve a set of state modifications. Each state of an open
+automaton has a set of \emph{state variables} that can be assigned by
+incoming transitions. Strictly speaking, the LTSs at the leaves of the
+open automaton are a restricted form of pLTSs, where labels are
+parametrised actions, but include no guard nor assignments.
+
+\begin{definition}[Open transitions]
+	\label{def:OpenTransitions}
+	An \emph{open transition} $OT$ over
+        % a set  $\langle S_i,s_{0 i}, \rightarrow_i\rangle^{i\in I}$ of LTSs,
+        a set $J$ of holes, %with sorts $Sort_j^{j\in J}$
+        and a set of states $\mathcal{S}$ is a structure of the form:	
+	\begin{mathpar}
+	\inferrule*[myfraction=\reddottedrule]
+	{%\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
+		\{\xrightarrow{\beta_j}_j\}^{j\in J}, \Pred\,, \Post}
+	{s \xrightarrow {\alpha}s'}\,,
+	\end{mathpar}
+	where $s, s'\in\mathcal{S}$, the $a_i, \beta_j, \alpha$ are
+        action expressions,
+        % $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the 
+	% LTS $\langle S_i,s_{0 i}, \rightarrow_i\rangle$
+        $\beta_j$
+        is an action of the hole $j$, and $\alpha$ is the resulting action
+        of $OT$. \Pred\ is a predicate
+	over the variables of the terms, labels, and states $s_i$,
+        $\beta_j$, $s$, $\alpha$. \Post\ is a set of equations that  
+	hold \emph{after the open transition}, represented as a
+        substitution $\{x_k\gets e_k\}^{k\in K}$  
+	where $x_k$ are variables of $s'$ and $s'_i$, whereas $e_k$ are
+        expressions over the other variables of the open transition.
+\end{definition}
+
+\begin{definition}[Open automaton]
+	\label{def:open-automaton}
+	An \emph{open automaton} is a structure\\ $A =
+	\langle J,\mathcal{S},s_0,\mathcal{T}\rangle$ where:
+	\begin{itemize}
+		\item[$\bullet$]  $I$ and $J$ are  sets of indices,
+	%	\item[$\bullet$]  $LTS_i^{i\in I}$ is a family of LTSs,
+		\item[$\bullet$]  $\mathcal{S}$ is a set of states and $s_0 \in \mathcal{S}$ the initial state,
+		\item[$\bullet$] $\mathcal{T}$ is a set of open transitions and, for each
+		$t\in \mathcal{T}$, there exist $I'$, $J'$ with $I'\subseteq I$, $J'
+		\subseteq J$, such that $t$ is an open transition over $J'$,
+		and  $\mathcal{S}$.
+
+	\end{itemize}
+\end{definition}
+
+%
+%Then the semantics of a pNet is characterized by a set of {\em open
+%transitions}, where the hypotheses on process parameters are
+%replaced by 1) transitions of the pLTSs at the leaves, and 2) formal
+%hypotheses on the transitions of the holes. A {\em predicate} is used
+%to relate the parameters and names appearing in the actions of the
+%leaves and the holes involved in the rules, but also appearing in  the resulting action.
+
+% \TODO{Relate to the algorithm, or even move to section 5}
+The \emph{states} and the shape of \emph{predicates} in the
+transitions
+of an open automaton representing the semantics of a pNet
+have the following specific structure.
+
+\paragraph{States of open pNets.}\label{def-states}
+  A state of an open pNet is a tuple of the
+  states of its leaves (in which we denote tuples
+  in structured states as $\triangleleft\ldots\triangleright$).
+  For any pNet p, let $\overline{\mathit{Leaves}} = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be the set of pLTS at its leaves,
+  then $\mathit{States}(p) = \{\ostate{s_i^{i\in L}}
+  |\, \forall i\in L. s_i \in S_i\}$.
+A pLTS being its own single leave:
+  $\mathit{States}(\mylangle S,s_0, \to\myrangle) = \{\ostate{s}|\, s \in S\}$.
+The initial state is defined as:
+$\mathit{InitState}(p) = \ostate{{{s_i}_0}^{i\in L}}$.
+
+%% \begin{example} \emph{State of a pNet}
+%%   The states of pNet \texttt{EnableCompL} are:
+%%   $\triangleleft 00 \triangleright, \triangleleft 10 \triangleright, \triangleleft 11 \triangleright$
+%% \end{example}
+
+\paragraph{Predicates.}
+Let
+$\mylangle\overline{\pNet},J,\symb{SV}_k^{k\in K} \myrangle$
+be a pNet. Consider a synchronization vector $SV_k$, for $k\in K$. We build a
+predicate $\MkPred$ relating
+the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
+\begin{multline*}
+  \MkPred(SV_k, a_i^{i\in I}, b_j^{j\in J}, v)\Longleftrightarrow
+  %% \begin{array}{l}
+  \exists {(a'_i)}^{i\in I},
+          {(b'_j)}^{j\in J},v'.\\
+          SV_k={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v'
+          \land
+          \forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v'
+\end{multline*}
+
+%% \end{array}
+
+%% This definition is not constructive but it is easy to build the
+%% predicate constructively by brute-force unification of the sub-pNets
+%% actions with the corresponding vector actions, possibly followed by a simplification
+%% step.
+
+\begin{example}[An open transition]\TODO{change for Enable example}
+  Transition $OT_1$ of the pNet $EnableCompl$ is generated by
+  combination of the first vector of its root node, with
+  the second vector of its $2^{nd}$ node. Its generated predicate is
+  trivialy true. The global states shows that controler $C_3$ has
+    changed from state 0 to 1.
+
+    \TODO{add another example to illustrate assignements/Post}
+
+  \label{OT:example-1}
+        \begin{mathpar}
+	  OT_1  =
+          \inferrule*[myfraction=\reddottedrule]
+	{\{\xrightarrow{\delta(x3)}_P ~~
+          \xrightarrow{acc(x3)}_Q \} ~~
+          [\forall z. acc(x3) \neq \delta(z)]
+        }
+	{\ostate{0,0} \xrightarrow {\underline{\delta(x3)}} \ostate{1,0}}
+	\end{mathpar}
+\end{example}
+
+\paragraph{Structural Semantic Rules:}
+The semantics of pNet in term of open automata has been defined in
+\cite{henrio:Forte2016}, in the form of 2 structural rules, one for
+pLTSs, one for pNet nodes. These rules are slightly improved, adding guards in the synchronisation vectors and syntax for universal quantifier in the guards (see~\cite{Avocs-RR}).
+
+In \cite{henrio:Forte2016} we also proved:
+\begin{theorem}[Finiteness]
+  \label{Th:finiteness}
+  Given an open pNet $pnet=\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $l_i^{i\in I}$ and holes $h_j^{j\in
+  J}$, if the sets $I$ and $J$ are finite, if the synchronisation vectors of all pNets 
+  included in  $pnet$   are finite, and if
+$\forall i \in L.\, finite{(states(l_i))} \text{ and } l_i$
+has a finite number of state variables, then its semantics is an open automaton 
+$\mathcal{T}$ with finitely many states and transitions.
+\end{theorem}
+  Remark that all the elements of such pNets and open automata being
+symbolic, they can represent many classes of unbounded systems.
+
+\begin{proof}
+  \TODO{I tentatively copied the proof here, from RR-8898.
+the proof of the finiteness theorem refers to SOS rules Tr1 and
+  Tr2. So maybe we must include (and explain) these here. One problem
+  is that these rules have been modified/improved with each new
+  publication of pNets papers, so we have to decide which version we
+  use here
+    Then we should
+    check if it is sufficient with this version of the algorithm, or
+    if it can be make more precise (some added analysis of the
+    behavior of matching/combining/filetring ?)}
+  The possible set of states of the open-automaton is the cartesian
+  product of the states of its leaves $pLTS_i^{i\in L}$, that is finite by
+  hypothesis. So the top-level residual loop of Algorithm 1 terminates provided each 
+  iteration terminates. The enumeration of open-transitions in step 2b is bounded by the
+  number of applications of rules Tr2 on the structure of the
+  pNet tree, with a finite number of synchronisation vectors applying
+  at each node the number of global open transition is finite. Similarily rule Tr1 is 
+  applied finitely if the number
+  of transitions of each pLTS is finite. So we get finitely many deduction trees, and
+  open-transitions which ensures that each internal loop of Algorithm 1 terminates.
+  \end{proof}
+
+\section{Generation of Open Automata}
+\label{section:implementation}
+In this section we describe the algorithm implementing the pNet
+semantics, the interaction with the Z3 SMT solver, and we show the
+result on our example. Under the hypotheses of Theorem \ref{Th:finiteness}
+this algorithm terminates.
+
+%% \noteSB{
+%% line 11: Would it not be better to prune unsatisfiable transitions
+%% on-the-fly, \ie inside the loop?}
+%% \noteEM{Not so easy, it would require a proof... on one side this
+%%   would implement reachability on the fly; but there is the question
+%%   of collecting the assignments of the state variables, that are used
+%%   in the sat check !}
+
+\begin{algorithm}[h]
+  \caption{Open Automaton Generation}
+  \label{alg1}
+\begin{algorithmic}[1]
+\Require A pNet $P$ (can be a pLTS, but not a hole)
+        %\qquad \hl{\textbackslash\textbackslash~SB: was `` pn ''}
+\State Initialize sets $U=\{\mathit{InitState}(P)\}$ and $E=\emptyset$,
+for unexplored and explored global states, respectively; $L=\emptyset$ for the resulting OTs;
+\While{!$\mathit{isEmpty}(U)$}
+	\State Choose $S$ in $U$; remove $S$ from $U$, add $S$ to $E$;
+        %\qquad \hl{\textbackslash\textbackslash~SB: was `` Choose $S$ in $U$ ''}
+	\State $\mathit{OTs} = \mathit{MakeTransitions}(P, S)$;
+	\For {each $\mathit{OT} \in \mathit{OTs}$}
+          \State Add $\mathit{OT}$ to $L$;
+          \State Let $S'$ be the target state of $\mathit{OT}$
+          Add $S'$ to the unexplored states if necessary:
+	  \IfThen{($S' \not\in U \cup E$)}{Add $S'$ into $U$;}
+	  \EndFor
+\EndWhile
+\State \ERIC{Prune the unsatisfiable open transitions in $L$ using the SMT
+solver; only keep reachable global states;}
+\State \Return $\mathit{OA}=(\mathit{InitState}(P),L)$;
+
+\end{algorithmic}  
+\end{algorithm}
+
+Algorithm~\ref{alg1} starts with an open pNet, and builds its set of open
+transitions. Its main loop is a classical residual algorithm: starting
+from the initial global state, it picks a state in an unexplored set, and
+computes all possible OTs, adding their target states in the
+unexplored set, until this set is empty.
+
+\ERIC{Before the SAT checking step, it may contain symbolic transitions that
+do not have valid ground instanciations. This is not logicaly
+incorrect, but is naturaly not an optimal representation. So we prune
+these UNSAT transitions: at the root of the pNet, the predicate of each OT is translated
+into SMTlib assertions, and checked for satisfiability.
+The final open automaton includes all satisfiable OTs, and the set of
+reachable global states.}
+%By construction, due to the
+%satisfiability test in line 6, it only produces the set of states reachable
+%through a sequence of satisfiable open transitions.
+
+The inside loop (\emph{MakeTransitions} method) applies recursively
+the semantic rules following the structure of the pNet.
+When applied to a pLTSs at the leaves, we simply take the pLTS transitions of the
+corresponding local state and use the semantic rule to build the OT\footnote{%
+%
+  We omit detailed presentation of this case for the sake of brevity.
+%
+}.
+When applied to a pNet node we use two methods, combining and
+matching, to generate the open transitions in a hierarchical manner,
+as shown in Alg.~\ref{alg2}. This method directly manages the
+holes of the node, so \emph{MakeTransitions} is never called on a hole.
+
+%
+%% \noteInSB{Algorithm~\ref{alg2}, as presented below is not
+%%   well-defined: when we reach the leaves, a pLTS does not have any
+%%   subnets, hence the loop in lines 2--4 is empty and so is the list
+%%   $l$. $\mathit{Combining}(l)$ is then called on an empty list...}
+
+%\noteInSB{Line 2: Tr1 and Tr2 are the semantic rules, right?}
+
+%% \noteInSB{Line 6: Nothing in the assignment $\overline{comb} =
+%%   \mathit{Combining}(l)$ depends on $sv$.  Hence, this should probably
+%%   be done outside of the loop.}
+
+%% \noteSB{Line 7: There are two type mismatches here: $ot$ is an open
+%%   transition, whereas $\mathit{Matching}$ is a predicate\mdash one
+%%   cannot assign a predicate to an open transition.  Furthermore, in
+%%   the definition of $\mathit{Matching}$, below, $C_n$ is an open
+%%   transition, whereas $\overline{comb}$ is a {\em set} of open
+%%   transitions, so this call does not type either. There is probably
+%%   another inner loop over all tuples of OTs in $\overline{comb}$; even
+%%   so the open transition has to be defined completely, not just the
+%%   predicate\mdash what is the value of $Post$ for the new transition?
+%%   Maybe $\mathit{Matching}$ should not be a predicate, but an OT?
+%%   Finally, how is $\mathit{hole}$? (I have removed $v$\mdash here and
+%%   in the parameters of the definition of the $\mathit{Matching}$
+%%   predicate, because the text in the paragraph ``Matching'' says that
+%%   $v$ is fresh.)}
+%% \noteEM{Done, please check the new version}
+
+%\noteInSB{Line 8: When is $\mathit{Filter}(ot)$ called?}
+
+\begin{algorithm}[h]
+\caption{MakeTransitions() \em{for a pNet node}}
+  \label{alg2}
+\begin{algorithmic}[1]
+\Require a pNet node $P$ with subnets $\overline{sn}$ and holes $\overline{hole}$; a global state $S$.
+\State Initialize empty list $l$ and set $L$ for sub-transitions and transitions, respectively;
+	\For{each $\mathit{Subnet}$ in $\overline{sn}$}
+        \hfill $\setminus \setminus$ Recursively apply the semantic rules on the subnets
+           \State Store $\mathit{MakeTransitions}(Subnet, S)$ in $l$;
+	\EndFor
+	\State $\overline{comb} = \mathit{Combining}(l)$;
+	\For{ each $sv \in SV$ and each $comb \in \overline{comb}$ }
+           \State $ot = \mathit{Matching}(sv, \overline{\mathit{comb}}, \overline{\mathit{hole}})$;
+           \IfThen{($ot$ is defined)}{Store $ot$ in $L$; ~~~ $\setminus \setminus$ if $\mathit{Matching}()$ succeeds}
+	\EndFor
+\State \Return $L$;
+\end{algorithmic}  
+\end{algorithm}
+
+%
+%For holes, their behaviour is unspecified, it doesn't have an exact
+%external presentation of action. We only give an action variable to each hole
+%and treat it as hole behaviour to suppose working status of the
+%hole.
+%% Here should have a constraint that this variable belongs to the sort of hole.
+%In every case, the hole behaviours are unchanged, so we
+%only make the combinations of subnets' open transitions. 
+%
+
+\def\inactive{\{-\}}
+\paragraph{Combining.}
+The combining method enumerates all the possible behaviours of the
+subnets as all the possible combinations of their open transitions.
+Assume that there is a collection of $n$ subnets.
+%% \noteSB{These variables are not used and conflict with the returned
+%%   set $L$ in Alg.~\ref{alg2}, on one hand, and control states $s_i$ of
+%%   the subnets, on the other.}
+%% \st{$L = {s_1, s_2, ...,  s_n}$;}
+We denote $\overline{ot}_i$ the set of open
+transitions of the $i$-th
+subnet (obtained in line~3 of the algorithm); %% $s_i$ and 
+``$-$'' means that the subnet is not involved.
+The combination $\overline{comb}$, a set of n-tuples, is the
+cartesian product:  
+$\overline{comb} = (\inactive\cup \overline{ot}_1) \times (\inactive\cup \overline{ot}_2)\times \dots \times (\inactive\cup \overline{ot}_n)$.
+
+%Algorithm 2 shows the combining algorithm for enumerating all possible
+%working status combinations from subnets. Dealing with a list $TR$
+%containing  sets of open transitions from different subnets,
+%the algorithm choses one of sets $L_{ot}$ and does combining on the
+%remaining part of $TR$ recursively. The case when a subnet is not working is
+%managed by adding a $null$ into the $L_{ot}$.
+
+\paragraph{Matching.}
+The \emph{Matching} method builds the OTs of a pNet node from those of
+its subnets.
+For each synchronisation vector and each possible
+combination of behaviours of the subnets, as generated by the \emph
+{Combining} method, it builds the corresponding open transition.
+Here, we only detail the construction of the predicate.
+From a synchronization vector
+$sv = \left((a'_i)^{i\in I} (b'_j)^{j\in J}\rightarrow v'\right) \in SV$
+and its guard $G_k$; a tuple of open transitions
+$C = ({ot}_i)^{i \in [1,n]} \in \overline{comb}$, such that, for each $i \in [1,n]$, either $ot_i = -$, or the result action of $ot_i$ is $a_i$; the hole behaviours $\mathit{Hole} = (b_j)^{j \in J}$; and a fresh variable $v$, representing the result action of the OT under construction, we build the predicate:
+%
+\begin{multline*}
+  \mathit{MkPred}(sv, C, \overline{\mathit{hole}}) = 
+  \\
+  (\forall i\in I, a_i=a'_i) \land
+%  (\forall i \not\in I, ot_i = -) \land
+  (\forall j\in J, b_j=b'_j) \land
+  (v=v') \land G_k.
+\end{multline*}
+
+\paragraph{Filtering.}
+While matching a vector with a combination tuple, \emph{Matching}
+tries to filter out some incompatibilities; there may be several
+reasons why the matching would fail: 
+\begin{itemize}
+  \item if some subnet is marked as inactive in the vector, and the
+    chosen combination has an active behaviour at this position,
+  \item if some subnet action expression in the vector does not match (by
+    pattern-matching) the corresponding action expression in $C$,
+  \item or if the whole set of active subnet actions in the vector
+    cannot be matched (by unification) with the corresponding action expressions
+      on the tuple $C$.
+\end {itemize}
+
+%\st{Each of these possible filters is more precise than the previous
+%  ones. But e}
+Even when unification succeeds, it is still possible that
+the resulting predicate would be unsatisfiable, because of some
+incompatibility involving the guards. In our algorithm, we choose to
+apply only the simplest filter inside the \emph{Matching} method
+(before applying the predicate and OT construction). Matching and
+unification  will be checked later, together with the guards collected
+from synchronisation vectors and from pLTS transtions, using the
+satisfiability check in the SMT engine.
+
+\subsection{Management of state variable assignments}
+
+In a pLTS, there may be several incoming transitions 
+that assign potentially different values to a state variable.
+To handle such cases, the algorithm manages, for each pLTS state, a
+list of expressions collected from the assignments of each state
+variable. %% $v$.
+%% The list we used contains triples <$v$, $S$, $AssignRH$> 
+%% where $v$ is the variable in pLTS, $S$ is its owner state and
+%% $AssignRH$ is a list of expressions over other variables in the right
+%% hand side of assignments of $v$.
+% As a pragmatic extension to the formal definition, we also manage
+% ``global variables'', defined in all states of the pLTS.
+For a global state in the open automaton, the set of state
+variables (which may be used in a transition) %% will simply be
+is the disjoint union
+of sets of state variables of the individual pLTS states constituting this
+global state.
+%There are some assignment on the variables in each of states of the pLTS (state variables), or just as global states of it (global variables).
+There is usually not only one assignment for a state variable, miss of them may drop the unsatisfiable results.
+In order to avoid such mistakes,
+\TODO{these assignment sets collect potential assignments from all OTs
+  in the generated automaton. If we minimize the generated state
+  space, we will get less assignements, and potentialy also get better
+  minimization... }
+
+%% \QIN{
+%% The list we used contains several triples <$v$, $S$, $AssignRH$> to
+%% record the information of both state and global variables of the pLTS,
+%% where $v$ is the variable in pLTS, $S$ is its owner state and
+%% $AssignRH$ is a list of expressions over other variables in the right
+%% hand side of assignments of $v$. It means the variable is global in
+%% the pLTS belonging to all the states, if $S$ is $null$. We update the
+%% list of record triples every time Tr1 is applied. Then we can track
+%% all the possible (symbolic) value of the variables when computing open transitions.
+%% }
+
+\subsection{Pruning the unsatisfiable results}
+\label{section:pruning}
+
+\begin{figure}[t]
+\begin{mathpar}
+    ot = \openrule{\{s0 \xrightarrow{fail(true)} s0, t0 \xrightarrow{resume(false)} t0\}, ~~\{\xrightarrow{hb}\},~~fail(true)=fail(b_1)\\
+    \OTland resume(false)=start(b_2)\OTland hb=fail(b_0)\OTland v=\underline{fail}\OTland b_1=b_2\\
+    \OTland (b_1\lor b_2) \Rightarrow b_0, ~~\{\}}
+    	   {\ostate{s0,t0} \xrightarrow{v} \ostate{s0,t0}}
+  \end{mathpar}
+\caption{One of the unsatisfiable open transitions \TODO{to be changed}}  \label{schema:unsat-ot}
+\end{figure}
+
+Our matching/filtering strategy builds some transitions where
+the predicates express incompatible constraints. Even if having an
+unsatisfiable (symbolic) transition would not be incorrect,
+we choose to minimize the open automaton (\ie its number of
+transitions and states), by checking the predicates for satisfiability.
+In Fig.~\ref{schema:unsat-ot}, we show an 
+unsatisfiable open transition 
+from the open automaton of our running example. It shows the case where
+the failure controller performs a ``$\PortFail$'' action, while the timer
+executes a ``$\PortResume$''. The chosen synchronization
+vector (SV0 from Fig.~\ref{schema:ArchFailure:pNet}) does not match
+with these actions, since it expects $\NameTimer.\PortStart$. This
+  mismatch is materialised by the predicate
+fragment ``$\mathit{resume}(\false)=\mathit{start}(b_2)$''.
+
+Checking satisfiability requires some symbolic computation
+on the action expressions and the predicates, which
+may depend on the specific theory of the action algebra datatypes. 
+The ``Modulo Theory'' part of SMT solvers is important here, so that
+the solver can use specific properties of each action algebra.
+
+\subsection{Computing reachable state space on the fly}
+\TODO{add a high level description of the new strategy, discuss
+  decidability/approximation of the SAT checking, express some
+  ``minimality'' property}
+
+The basic algorithm from the previous section potentialy explores some
+areas of the global state-space that will not be reachable after
+checking the OTs' predicates for satisfiability. Incorporating the
+satisfiability check inside the residual algorithm will definitely
+save some of these useless computation. More precisely, it will still
+create, and submit to Z3, the OTs at the ``border'' of the state-space, but
+not the transitions issued from non-reachable global states.
+
+\ERIC{But there is more to this. As mentionned above, we collect all
+possible (symbolic) assignments of state variables, in the
+computed open automaton. By avoiding building the OTs coming from
+unreachable states, we also avoid adding the corresponding assignments
+to the variables of their target states. The set of possible
+assignments is an over approximation of possible values of the
+variables of such state, so narrowing it means we get a better
+approximation, and potentialy more informations, that can be used to
+the SAT check of subsequent transitions.}
+\TODO{Beware, I think this is dangerous... Xudong, do we really use
+  assignment information in SAT checking ? In the ``smart'' version, I
+  think we must NOT use it, because we do not yet have collected all
+  possible assignments.}
+
+Algorithm~\ref{alg3} implement this new stategy: \TODO{Explain
+  significant detials}
+
+\begin{algorithm}[h]
+  \caption{``Smart'' Reachable Open Automaton Generation}
+  \label{alg3}
+\begin{algorithmic}[1]
+\Require A pNet $P$ (cannot be a hole)
+        %\qquad \hl{\textbackslash\textbackslash~SB: was `` pn ''}
+\State Initialize sets $U=\{\mathit{InitState}(P)\}$ and $E=\emptyset$,
+for unexplored and explored global states, respectively; $L=\emptyset$ for the resulting OTs;
+\While{!$\mathit{isEmpty}(U)$}
+	\State Choose $S$ in $U$; remove $S$ from $U$, add $S$ to $E$;
+        %\qquad \hl{\textbackslash\textbackslash~SB: was `` Choose $S$ in $U$ ''}
+	\State $\mathit{OTs} = \mathit{MakeTransitions}(P, S)$;
+%%        \State Store $\mathit{OT}$ in $L$; 
+	\For {each $\mathit{OT} \in \mathit{OTs}$}
+        Check satisfiability of $\mathit{OT}$ using the SMT solver;
+        \IfThen {$SAT(\mathit{OT})$}
+                {\State \{Add $\mathit{OT}$ to $L$;
+                  \State Let $S'$ be the target global state of $\mathit{OT}$
+	          \IfThen{($S' \not\in U \cup E$)}{Add $S'$ into $U$;}
+                  \}}
+	\EndFor
+\EndWhile
+%%\State Prune the unsatisfiable open transitions in $L$ using the SMT solver;
+\State \Return $\mathit{OA}=(\mathit{InitState}(P),L)$;
+
+\end{algorithmic}  
+\end{algorithm}
+
+\TODO{Candidate theorems:
+  - All reachable states from algorithm 1 are kept by Algorithm 3\\
+  - Algorithm 3 computes an open automaton that is minimal with
+  respect of SAT checking decidability.\\
+  I have problem with minimality... Because of the ``two phases'' SAT
+  checking that we have now, because we cannot use incomplete sets of
+  variable assignments during the ``smart'' phase, and use them later,
+minimality becoomes trivialy equivalent in the original and smart algorithms...}
+
+\subsection{Translation to SMTlib}
+
+We check the satisfiability of each open transitions
+using the SMT solver Z3.
+%More precisely, we translate
+%the OT predicate into an SMTlib assertion in the context provided by
+%the possible state variable assignments in the source state.
+In this
+section, we describe the translation of the algebra presentation, of
+assignments, and of the predicates.
+
+Our implementation submits satisfiability requests to
+Z3 using its JAVA API. Here, for readability, we
+show the Z3 code using its SMT-LIB input language.
+Note that in the previous sections, the OTs were displayed in a
+  simplified, human readable form. The input and output of our tool, and
+  also the generated SMTlib fragments, are
+  slightly more difficult to read, in 
+particular because of structured names for the fresh variables generated
+by the algorithm, allowing tracability of the result~\cite{Avocs-RR}.
+
+Figure~\ref{schema:smt-lib} shows the translation of the
+transition of Fig.~\ref{schema:unsat-ot}
+in the SMTlib syntax.
+It contains the declaration
+of the BIP action algebra sorts 
+and constructors, then the declaration of variables, and finally the
+predicate to be checked, encoded as a set of assertions.
+Here the behavior of the hole ``B'' appears as a variable
+``|hb\_B:13:1|'', and line 10 shows the constraint that matching with
+a synchronisation vector has imposed on the behavior of ``B''.
+Here we display also the diagnosis (``sat'' or ``unsat'') generated by Z3.
+
+\begin{figure}[t]
+  %  \centerline{\includegraphics[width=12cm]{XFIG/SMTLIB2}}
+    \centerline{\includegraphics[width=\linewidth]{XFIG/SMTLIB3}}
+  \caption{The input of the Z3 solver in SMT-LIB language and the output result\TODO{Change}}  \label{schema:smt-lib}
+\end{figure}
+
+By lack of space, we have only shown here a use-case with boolean data
+parameters, so we only require the basic SAT capability of the Z3
+engine. It should be clear that more involved examples will require
+reasonning on predicates of various data types. Z3 provides theories for reasonning
+on integers, bitstrings, enumerated types, arrays, etc.
+We also need to deal with some universal quantification on free
+variables occuring in the guards of synch vectors.
+For other data structures usual in such models, like records, or
+recursive structures, the user will have to develop its own theories.
+Decidability of these theories will condition the completeness of the
+satisfiability check, and the decidability of model-checking or
+bisimulation checking.
+
+%% \begin{figure}[t]
+%%   \centerline{\includegraphics[width=10cm]{XFIG/Interaction}}
+%%   \caption{The architecture of the interaction between pNet API and Z3}  \label{schema:interaction}
+%% \end{figure}
+
+\paragraph{Production of the SMT-lib code}
+  To build the input submitted to Z3 for each OT,
+we translate the algebra presentation, the predicates and the
+variable assignments into Z3 (Java-API) calls.
+% The $presentation$ and the predicates are translated separately.
+
+\emph{Translation of action algebra presentation.}
+In~\cite{Avocs-RR}, we  define the translation of an algebra presentation into
+SMTlib declarations (\texttt{declare-datatypes} and
+\texttt{declare-fun}). We also formalize a condition of well-formedness of pNets ensures that the generated code is correct,
+and will not raise runtime errors in the SMT engine. Note that the
+\texttt{declare-datatypes} command comprises both the action
+constructors from table \ref{table:BIPalgebra} and also the constant action
+names from our example.
+Additionally, we will include axiomatisation of any required functions
+and predicates of the presentation data-types.
+
+%% \paragraph{Translating assignments into predicate terms.}
+%% State variable assignments that were collected during the open
+%% automaton are used when generating the SMTlib asserts (see
+%% App.~\ref{appendix:translating-assignments}). \noteSB{I am not an expert of Z3 or SMT-LIB, but the clause '\texttt{(= t (- t 1))}' looks very suspicious to me.}\hl{This appears in
+%% line 10 of Fig.~\ref{schema:smt-lib}, which encodes possible values of
+%% the variable $t$ of the timer.}
+
+%The assignments are also taken into account when checking the
+%satisfiability of the open transitions as they represent the value of
+%the variables involved in an OT. In order to do that, we employs a
+%translation from assignments into term of predicates. The assignments
+%required to be translated are only those belong to the variables
+%contain in the start states of the open transitions. The assignments
+%are represented as equations between the variables and the expressions
+%on the right side of assignment. For the assignments of the same
+%variable, we do not figure out which state is the precursor of current
+%state, we keep all these possible equations instead, and generate the
+%disjunction of these equations. The state could always move to the
+%target state if there exists one of the values of its variable
+%satisfies the guard.
+%%\TODO{It won't matter the variable of the next state
+%%except that the right hand side expression contain its variables. This
+%%is a problem left to be solved in our future work. WHICH PROBLEM ?}
+%After that, for the assignments of the different variables, we generate a conjunction of them. This way we obtain a new term of the predicate involving assignments of the variables.
+
+%% State-variable assignments are also treated as a part of the
+%% predicates when checking the satisfiability. % Here we need conduct some
+%% % translations,
+%% For each assignement in a $\Post$ predicate, such as $\{s_0 \leftarrow 1\}$ in section
+%% ~\ref{section:op-semantics}, we translate it into an equation
+%% $s_0=1$. For several assignments of the same variable in the same state,
+%% we generate the disjunction of 
+%% these equations. Correspondingly, we generate a conjunction for the
+%% assignments from different variables.
+
+\emph{Translation of open transitions.}
+In~\cite{Avocs-RR} we formally define all steps of the translation of each
+open transition, including:
+%
+\begin{itemize}
+\item collect all variables in the transition, and declare them (using \texttt{declare-const})
+\item check well-formedness and correct typing of expressions,
+\item translate the predicate into a conjunction of assertions,
+\item if present in the source state, translate the state-variable
+  assignments into a disjunctive assertion.
+\end{itemize}
+%
+This translation ensures that no runtime error will occur
+in the SMT engine.
+
+Figure~\ref{schema:smt-lib} shows the decomposition of the
+predicate into a set of asserts, each encoding an elementary equality,
+inequality, or a guard. 
+The result (sat or unsat) of the final \texttt{check-sat} command in
+the translation () is then decoded.
+
+\section{Use-cases}
+\TODO{new section here, showing various features on different examples}
+
+\subsection{Enable operator} in Lotos, with (equivalent) state-based and data-based encodings; Associativity of Enable;
+
+\subsection{simple communication protocol} specification and implementation;
+
+\subsection{BIP FailureTimer architecture}
+
 \label{section:FailureTimerMax}
@@
 
-%% Several publications \cite{HMZ:PDP15,henrio:Forte2016} already have introduced
-%% many examples of pNets, encoding
-%% operators of various classical process algebras, or more complex
-%% synchronization structures in distributed or parallel languages.
-
-%% \TODO{1.5 page including figures ?}
-
-%% \TODO{Simon: can you do this in less than one page ? If you prefer,
-%%   merge with ``Running example'' may be easier to describe the syntax}
-
-%% \TODO{Simon: or may be better, present BIP architectures and the use-case \_BEFORE\_ The pNets definition, and define the encoding here}
-
-%% \TODO{Should have here both the original BIP drawing (Simon), and the
-%%   pNet encoding (fig by Eric)}
-
-\section{Operational Semantics for Open pNets}
-\label{section:op-semantics}
-
-The semantics of open pNets will be defined as an open automaton, that
-is an automaton where each transition composes transitions 
-of several
-% \noteSB{These should all be pLTSs, right? Or did I miss
-%  something?}\noteEM{Hum, nor really, something intermediate; the actions there can be
-%  parameterised actions, but the label has no guard and no
-%  assignments}
-LTSs with the actions of some holes; the transition occurs if some predicates hold,
-and can involve a set of state modifications. Each state of an open
-automaton has a set of \emph{state variables} that can be assigned by
-incoming transitions. Strictly speaking, the LTSs at the leaves of the
-open automaton are a restricted form of pLTSs, where labels are
-parametrised actions, but include no guard nor assignments.
-
-\begin{definition}[Open transitions]
-	\label{def:OpenTransitions}
-	An \emph{open transition} $OT$ over
-        % a set  $\langle S_i,s_{0 i}, \rightarrow_i\rangle^{i\in I}$ of LTSs,
-        a set $J$ of holes, %with sorts $Sort_j^{j\in J}$
-        and a set of states $\mathcal{S}$ is a structure of the form:	
-	\begin{mathpar}
-	\inferrule*[myfraction=\reddottedrule]
-	{%\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
-		\{\xrightarrow{\beta_j}_j\}^{j\in J}, \Pred\,, \Post}
-	{s \xrightarrow {\alpha}s'}\,,
-	\end{mathpar}
-	where $s, s'\in\mathcal{S}$, the $a_i, \beta_j, \alpha$ are
-        action expressions,
-        % $s_i{\xrightarrow{a_i}}_i s_i^{\prime}$ is a transition of the 
-	% LTS $\langle S_i,s_{0 i}, \rightarrow_i\rangle$
-        $\beta_j$
-        is an action of the hole $j$, and $\alpha$ is the resulting action
-        of $OT$. \Pred\ is a predicate
-	over the variables of the terms, labels, and states $s_i$,
-        $\beta_j$, $s$, $\alpha$. \Post\ is a set of equations that  
-	hold \emph{after the open transition}, represented as a
-        substitution $\{x_k\gets e_k\}^{k\in K}$  
-	where $x_k$ are variables of $s'$ and $s'_i$, whereas $e_k$ are
-        expressions over the other variables of the open transition.
-\end{definition}
-
-\begin{definition}[Open automaton]
-	\label{def:open-automaton}
-	An \emph{open automaton} is a structure\\ $A =
-	\langle J,\mathcal{S},s_0,\mathcal{T}\rangle$ where:
-	\begin{itemize}
-		\item[$\bullet$]  $I$ and $J$ are  sets of indices,
-	%	\item[$\bullet$]  $LTS_i^{i\in I}$ is a family of LTSs,
-		\item[$\bullet$]  $\mathcal{S}$ is a set of states and $s_0 \in \mathcal{S}$ the initial state,
-		\item[$\bullet$] $\mathcal{T}$ is a set of open transitions and, for each
-		$t\in \mathcal{T}$, there exist $I'$, $J'$ with $I'\subseteq I$, $J'
-		\subseteq J$, such that $t$ is an open transition over $J'$,
-		and  $\mathcal{S}$.
-
-	\end{itemize}
-\end{definition}
-
-%
-%Then the semantics of a pNet is characterized by a set of {\em open
-%transitions}, where the hypotheses on process parameters are
-%replaced by 1) transitions of the pLTSs at the leaves, and 2) formal
-%hypotheses on the transitions of the holes. A {\em predicate} is used
-%to relate the parameters and names appearing in the actions of the
-%leaves and the holes involved in the rules, but also appearing in  the resulting action.
-
-% \TODO{Relate to the algorithm, or even move to section 5}
-The \emph{states} and the shape of \emph{predicates} in the
-transitions
-of an open automaton representing the semantics of a pNet
-have the following specific structure.
-
-\paragraph{States of open pNets.}\label{def-states}
-  A state of an open pNet is a tuple of the
-  states of its leaves (in which we denote tuples
-  in structured states as $\triangleleft\ldots\triangleright$).
-  For any pNet p, let $\overline{\mathit{Leaves}} = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be the set of pLTS at its leaves,
-  then $\mathit{States}(p) = \{\ostate{s_i^{i\in L}}
-  |\, \forall i\in L. s_i \in S_i\}$.
-A pLTS being its own single leave:
-  $\mathit{States}(\mylangle S,s_0, \to\myrangle) = \{\ostate{s}|\, s \in S\}$.
-The initial state is defined as:
-$\mathit{InitState}(p) = \ostate{{{s_i}_0}^{i\in L}}$.
-
-%% \begin{example} \emph{State of a pNet}
-%%   The states of pNet \texttt{EnableCompL} are:
-%%   $\triangleleft 00 \triangleright, \triangleleft 10 \triangleright, \triangleleft 11 \triangleright$
-%% \end{example}
-
-\paragraph{Predicates.}
-Let
-$\mylangle\overline{\pNet},J,\symb{SV}_k^{k\in K} \myrangle$
-be a pNet. Consider a synchronization vector $SV_k$, for $k\in K$. We build a
-predicate $\MkPred$ relating
-the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
-\begin{multline*}
-  \MkPred(SV_k, a_i^{i\in I}, b_j^{j\in J}, v)\Longleftrightarrow
-  %% \begin{array}{l}
-  \exists {(a'_i)}^{i\in I},
-          {(b'_j)}^{j\in J},v'.\\
-          SV_k={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v'
-          \land
-          \forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v'
-\end{multline*}
-
-%% \end{array}
-
-%% This definition is not constructive but it is easy to build the
-%% predicate constructively by brute-force unification of the sub-pNets
-%% actions with the corresponding vector actions, possibly followed by a simplification
-%% step.
-
-\begin{example}[An open transition]
-  This transition is generated by application of the vector \texttt{SV0},
-  synchronizing the initial actions of pLTSs \texttt{Control} and
-  \texttt{Timer} (see Fig.~\ref{schema:ArchFailure:pNet}), with an action of the hole \texttt{B} equal to
-  \texttt{fail}. The local variable \texttt{t} of the \texttt{Timer}
-  is assigned to its initial value \texttt{Max}.
- A full output of 
-the use-case is provided in~\cite{Avocs-RR}.
-
-  \label{OT:example-1}
-        \begin{mathpar}
-	\inferrule*[myfraction=\reddottedrule]
-	{\{s0~{\xrightarrow{\mathit{fail}(\true)}} ~s1, t0~{\xrightarrow{\mathit{start}(\true)}} ~t1\}
-	  \{\xrightarrow{\mathit{hb}}\}, \mathit{hb}=\mathit{fail}(\true) \land v=\underline{\mathit{fail}}, \{t := \mathit{Max}\}
-        }
-	{\ostate{s0,t0} \xrightarrow {v} \ostate{s1,t1}}
-	\end{mathpar}
-\end{example}
-%
-%The open transition $ot_2$ involves the possible actions from the process $P$ and prefix expression $acc(x);Q$.
-The hole behaviour, represented by variable $hb_{12}$ must be equal to the exit action $\delta(x)$, and the accept event $acc(x)$ will capture the same value $x$.
-%
-%The transition in the conclusion of this rule starts in
-%state $\ostate{00}$, where both $C_1$ and $C_2$ are in their initial
-%states. It ends in a different structured state, because in $ot_2$
-%both pLTS conduct transitions, showing that the control has gone from
-%processes $P$ to $(acc(x);Q$, consuming actions $\delta(x)$ and
-%$acc(x)$. Controller $C_1$ has only one state, but its state variable
-%$s_0$ has changed to 1.
-
-\paragraph{Structural Semantic Rules:}
-The semantics of pNet in term of open automata has been defined in
-\cite{henrio:Forte2016}, in the form of 2 structural rules, one for
-pLTSs, one for pNet nodes. These rules are slightly improved, adding guards in the synchronisation vectors and syntax for universal quantifier in the guards (see~\cite{Avocs-RR}).
-
-\TODO{the proof of the finiteness theorem refers to SOS rules Tr1 and
-  Tr2. So maybe we must include (and explain) these here. One problem
-  is that these rules have been modified/improved with each new
-  publication of pNets papers, so we have to decide which version we
-  use here}
-
-In \cite{henrio:Forte2016} we also proved:
-\begin{theorem}[Finiteness]
-  \label{Th:finiteness}
-  Given an open pNet $pnet=\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $l_i^{i\in I}$ and holes $h_j^{j\in
-  J}$, if the sets $I$ and $J$ are finite, if the synchronisation vectors of all pNets 
-  included in  $pnet$   are finite, and if
-$\forall i \in L.\, finite{(states(l_i))} \text{ and } l_i$
-has a finite number of state variables, then its semantics is an open automaton 
-$\mathcal{T}$ with finitely many states and transitions.
-\end{theorem}
-  Remark that all the elements of such pNets and open automata being
-symbolic, they can represent many classes of unbounded systems.
-
-\begin{proof}
-  \TODO{I tentatively copied the proof here, from RR-8898. We should
-    check if it is sufficient with this version of the algorithm, or
-    if it can be make more precise (some added analysis of the
-    behavior of matching/combining/filetring ?)}
-  The possible set of states of the open-automaton is the cartesian
-  product of the states of its leaves $pLTS_i^{i\in L}$, that is finite by
-  hypothesis. So the top-level residual loop of Algorithm 1 terminates provided each 
-  iteration terminates. The enumeration of open-transitions in step 2b is bounded by the
-  number of applications of rules Tr2 on the structure of the
-  pNet tree, with a finite number of synchronisation vectors applying
-  at each node the number of global open transition is finite. Similarily rule Tr1 is 
-  applied finitely if the number
-  of transitions of each pLTS is finite. So we get finitely many deduction trees, and
-  open-transitions which ensures that each internal loop of Algorithm 1 terminates.
-  \end{proof}
-
-\section{Generation of Open Automata}
-\label{section:implementation}
-In this section we describe the algorithm implementing the pNet
-semantics, the interaction with the Z3 SMT solver, and we show the
-result on our example. Under the hypotheses of Theorem \ref{Th:finiteness}
-this algorithm terminates.
-
-%% \noteSB{
-%% line 11: Would it not be better to prune unsatisfiable transitions
-%% on-the-fly, \ie inside the loop?}
-%% \noteEM{Not so easy, it would require a proof... on one side this
-%%   would implement reachability on the fly; but there is the question
-%%   of collecting the assignments of the state variables, that are used
-%%   in the sat check !}
-
-\begin{algorithm}[h]
-  \caption{Open Automaton Generation}
-  \label{alg1}
-\begin{algorithmic}[1]
-\Require A pNet $P$ (can be a pLTS, but not a hole)
-        %\qquad \hl{\textbackslash\textbackslash~SB: was `` pn ''}
-\State Initialize sets $U=\{\mathit{InitState}(P)\}$ and $E=\emptyset$,
-for unexplored and explored global states, respectively; $L=\emptyset$ for the resulting OTs;
-\While{!$\mathit{isEmpty}(U)$}
-	\State Choose $S$ in $U$; remove $S$ from $U$, add $S$ to $E$;
-        %\qquad \hl{\textbackslash\textbackslash~SB: was `` Choose $S$ in $U$ ''}
-	\State $\mathit{OTs} = \mathit{MakeTransitions}(P, S)$;
-	\For {each $\mathit{OT} \in \mathit{OTs}$}
-          \State Add $\mathit{OT}$ to $L$;
-          \State Let $S'$ be the target state of $\mathit{OT}$
-          Add $S'$ to the unexplored states if necessary:
-	  \IfThen{($S' \not\in U \cup E$)}{Add $S'$ into $U$;}
-	  \EndFor
-\EndWhile
-\State \ERIC{Prune the unsatisfiable open transitions in $L$ using the SMT
-solver; only keep reachable global states;}
-\State \Return $\mathit{OA}=(\mathit{InitState}(P),L)$;
-
-\end{algorithmic}  
-\end{algorithm}
-
-Algorithm~\ref{alg1} starts with an open pNet, and builds its set of open
-transitions. Its main loop is a classical residual algorithm: starting
-from the initial global state, it picks a state in an unexplored set, and
-computes all possible OTs, adding their target states in the
-unexplored set, until this set is empty.
-
-\ERIC{Before the SAT checking step, it may contain symbolic transitions that
-do not have valid ground instanciations. This is not logicaly
-incorrect, but is naturaly not an optimal representation. So we prune
-these UNSAT transitions: at the root of the pNet, the predicate of each OT is translated
-into SMTlib assertions, and checked for satisfiability.
-The final open automaton includes all satisfiable OTs, and the set of
-reachable global states.}
-%By construction, due to the
-%satisfiability test in line 6, it only produces the set of states reachable
-%through a sequence of satisfiable open transitions.
-
-The inside loop (\emph{MakeTransitions} method) applies recursively
-the semantic rules following the structure of the pNet.
-When applied to a pLTSs at the leaves, we simply take the pLTS transitions of the
-corresponding local state and use the semantic rule to build the OT\footnote{%
-%
-  We omit detailed presentation of this case for the sake of brevity.
-%
-}.
-When applied to a pNet node we use two methods, combining and
-matching, to generate the open transitions in a hierarchical manner,
-as shown in Alg.~\ref{alg2}. This method directly manages the
-holes of the node, so \emph{MakeTransitions} is never called on a hole.
-
-%
-%% \noteInSB{Algorithm~\ref{alg2}, as presented below is not
-%%   well-defined: when we reach the leaves, a pLTS does not have any
-%%   subnets, hence the loop in lines 2--4 is empty and so is the list
-%%   $l$. $\mathit{Combining}(l)$ is then called on an empty list...}
-
-%\noteInSB{Line 2: Tr1 and Tr2 are the semantic rules, right?}
-
-%% \noteInSB{Line 6: Nothing in the assignment $\overline{comb} =
-%%   \mathit{Combining}(l)$ depends on $sv$.  Hence, this should probably
-%%   be done outside of the loop.}
-
-%% \noteSB{Line 7: There are two type mismatches here: $ot$ is an open
-%%   transition, whereas $\mathit{Matching}$ is a predicate\mdash one
-%%   cannot assign a predicate to an open transition.  Furthermore, in
-%%   the definition of $\mathit{Matching}$, below, $C_n$ is an open
-%%   transition, whereas $\overline{comb}$ is a {\em set} of open
-%%   transitions, so this call does not type either. There is probably
-%%   another inner loop over all tuples of OTs in $\overline{comb}$; even
-%%   so the open transition has to be defined completely, not just the
-%%   predicate\mdash what is the value of $Post$ for the new transition?
-%%   Maybe $\mathit{Matching}$ should not be a predicate, but an OT?
-%%   Finally, how is $\mathit{hole}$? (I have removed $v$\mdash here and
-%%   in the parameters of the definition of the $\mathit{Matching}$
-%%   predicate, because the text in the paragraph ``Matching'' says that
-%%   $v$ is fresh.)}
-%% \noteEM{Done, please check the new version}
-
-%\noteInSB{Line 8: When is $\mathit{Filter}(ot)$ called?}
-
-\begin{algorithm}[h]
-\caption{MakeTransitions() \em{for a pNet node}}
-  \label{alg2}
-\begin{algorithmic}[1]
-\Require a pNet node $P$ with subnets $\overline{sn}$ and holes $\overline{hole}$; a global state $S$.
-\State Initialize empty list $l$ and set $L$ for sub-transitions and transitions, respectively;
-	\For{each $\mathit{Subnet}$ in $\overline{sn}$}
-        \hfill $\setminus \setminus$ Recursively apply the semantic rules on the subnets
-           \State Store $\mathit{MakeTransitions}(Subnet, S)$ in $l$;
-	\EndFor
-	\State $\overline{comb} = \mathit{Combining}(l)$;
-	\For{ each $sv \in SV$ and each $comb \in \overline{comb}$ }
-           \State $ot = \mathit{Matching}(sv, \overline{\mathit{comb}}, \overline{\mathit{hole}})$;
-           \IfThen{($ot$ is defined)}{Store $ot$ in $L$; ~~~ $\setminus \setminus$ if $\mathit{Matching}()$ succeeds}
-	\EndFor
-\State \Return $L$;
-\end{algorithmic}  
-\end{algorithm}
-
-%
-%For holes, their behaviour is unspecified, it doesn't have an exact
-%external presentation of action. We only give an action variable to each hole
-%and treat it as hole behaviour to suppose working status of the
-%hole.
-%% Here should have a constraint that this variable belongs to the sort of hole.
-%In every case, the hole behaviours are unchanged, so we
-%only make the combinations of subnets' open transitions. 
-%
-
-\def\inactive{\{-\}}
-\paragraph{Combining.}
-The combining method enumerates all the possible behaviours of the
-subnets as all the possible combinations of their open transitions.
-Assume that there is a collection of $n$ subnets.
-%% \noteSB{These variables are not used and conflict with the returned
-%%   set $L$ in Alg.~\ref{alg2}, on one hand, and control states $s_i$ of
-%%   the subnets, on the other.}
-%% \st{$L = {s_1, s_2, ...,  s_n}$;}
-We denote $\overline{ot}_i$ the set of open
-transitions of the $i$-th
-subnet (obtained in line~3 of the algorithm); %% $s_i$ and 
-``$-$'' means that the subnet is not involved.
-The combination $\overline{comb}$, a set of n-tuples, is the
-cartesian product:  
-$\overline{comb} = (\inactive\cup \overline{ot}_1) \times (\inactive\cup \overline{ot}_2)\times \dots \times (\inactive\cup \overline{ot}_n)$.
-
-%Algorithm 2 shows the combining algorithm for enumerating all possible
-%working status combinations from subnets. Dealing with a list $TR$
-%containing  sets of open transitions from different subnets,
-%the algorithm choses one of sets $L_{ot}$ and does combining on the
-%remaining part of $TR$ recursively. The case when a subnet is not working is
-%managed by adding a $null$ into the $L_{ot}$.
-
-\paragraph{Matching.}
-The \emph{Matching} method builds the OTs of a pNet node from those of
-its subnets.
-For each synchronisation vector and each possible
-combination of behaviours of the subnets, as generated by the \emph
-{Combining} method, it builds the corresponding open transition.
-Here, we only detail the construction of the predicate.
-From a synchronization vector
-$sv = \left((a'_i)^{i\in I} (b'_j)^{j\in J}\rightarrow v'\right) \in SV$
-and its guard $G_k$; a tuple of open transitions
-$C = ({ot}_i)^{i \in [1,n]} \in \overline{comb}$, such that, for each $i \in [1,n]$, either $ot_i = -$, or the result action of $ot_i$ is $a_i$; the hole behaviours $\mathit{Hole} = (b_j)^{j \in J}$; and a fresh variable $v$, representing the result action of the OT under construction, we build the predicate:
-%
-\begin{multline*}
-  \mathit{MkPred}(sv, C, \overline{\mathit{hole}}) = 
-  \\
-  (\forall i\in I, a_i=a'_i) \land
-%  (\forall i \not\in I, ot_i = -) \land
-  (\forall j\in J, b_j=b'_j) \land
-  (v=v') \land G_k.
-\end{multline*}
-
-\paragraph{Filtering.}
-While matching a vector with a combination tuple, \emph{Matching}
-tries to filter out some incompatibilities; there may be several
-reasons why the matching would fail: 
-\begin{itemize}
-  \item if some subnet is marked as inactive in the vector, and the
-    chosen combination has an active behaviour at this position,
-  \item if some subnet action expression in the vector does not match (by
-    pattern-matching) the corresponding action expression in $C$,
-  \item or if the whole set of active subnet actions in the vector
-    cannot be matched (by unification) with the corresponding action expressions
-      on the tuple $C$.
-\end {itemize}
-
-%\st{Each of these possible filters is more precise than the previous
-%  ones. But e}
-Even when unification succeeds, it is still possible that
-the resulting predicate would be unsatisfiable, because of some
-incompatibility involving the guards. In our algorithm, we choose to
-apply only the simplest filter inside the \emph{Matching} method
-(before applying the predicate and OT construction). Matching and
-unification  will be checked later, together with the guards collected
-from synchronisation vectors and from pLTS transtions, using the
-satisfiability check in the SMT engine.
-
-\subsection{Management of state variable assignments}
-
-In a pLTS, there may be several incoming transitions 
-that assign potentially different values to a state variable.
-To handle such cases, the algorithm manages, for each pLTS state, a
-list of expressions collected from the assignments of each state
-variable. %% $v$.
-%% The list we used contains triples <$v$, $S$, $AssignRH$> 
-%% where $v$ is the variable in pLTS, $S$ is its owner state and
-%% $AssignRH$ is a list of expressions over other variables in the right
-%% hand side of assignments of $v$.
-% As a pragmatic extension to the formal definition, we also manage
-% ``global variables'', defined in all states of the pLTS.
-For a global state in the open automaton, the set of state
-variables (which may be used in a transition) %% will simply be
-is the disjoint union
-of sets of state variables of the individual pLTS states constituting this
-global state.
-%There are some assignment on the variables in each of states of the pLTS (state variables), or just as global states of it (global variables).
-There is usually not only one assignment for a state variable, miss of them may drop the unsatisfiable results.
-In order to avoid such mistakes,
-\TODO{these assignment sets collect potential assignments from all OTs
-  in the generated automaton. If we minimize the generated state
-  space, we will get less assignements, and potentialy also get better
-  minimization... }
-
-%% \QIN{
-%% The list we used contains several triples <$v$, $S$, $AssignRH$> to
-%% record the information of both state and global variables of the pLTS,
-%% where $v$ is the variable in pLTS, $S$ is its owner state and
-%% $AssignRH$ is a list of expressions over other variables in the right
-%% hand side of assignments of $v$. It means the variable is global in
-%% the pLTS belonging to all the states, if $S$ is $null$. We update the
-%% list of record triples every time Tr1 is applied. Then we can track
-%% all the possible (symbolic) value of the variables when computing open transitions.
-%% }
-
-\subsection{Pruning the unsatisfiable results}
-\label{section:pruning}
-
-\begin{figure}[t]
-\begin{mathpar}
-    ot = \openrule{\{s0 \xrightarrow{fail(true)} s0, t0 \xrightarrow{resume(false)} t0\}, ~~\{\xrightarrow{hb}\},~~fail(true)=fail(b_1)\\
-    \OTland resume(false)=start(b_2)\OTland hb=fail(b_0)\OTland v=\underline{fail}\OTland b_1=b_2\\
-    \OTland (b_1\lor b_2) \Rightarrow b_0, ~~\{\}}
-    	   {\ostate{s0,t0} \xrightarrow{v} \ostate{s0,t0}}
-  \end{mathpar}
-\caption{One of the unsatisfiable open transitions in the Failure Monitor pNet}  \label{schema:unsat-ot}
-\end{figure}
-
-Our matching/filtering strategy builds some transitions where
-the predicates express incompatible constraints. Even if having an
-unsatisfiable (symbolic) transition would not be incorrect,
-we choose to minimize the open automaton (\ie its number of
-transitions and states), by checking the predicates for satisfiability.
-In Fig.~\ref{schema:unsat-ot}, we show an 
-unsatisfiable open transition 
-from the open automaton of our running example. It shows the case where
-the failure controller performs a ``$\PortFail$'' action, while the timer
-executes a ``$\PortResume$''. The chosen synchronization
-vector (SV0 from Fig.~\ref{schema:ArchFailure:pNet}) does not match
-with these actions, since it expects $\NameTimer.\PortStart$. This
-  mismatch is materialised by the predicate
-fragment ``$\mathit{resume}(\false)=\mathit{start}(b_2)$''.
-
-Checking satisfiability requires some symbolic computation
-on the action expressions and the predicates, which
-may depend on the specific theory of the action algebra datatypes. 
-The ``Modulo Theory'' part of SMT solvers is important here, so that
-the solver can use specific properties of each action algebra.
-
-\subsection{Computing reachable state space on the fly}
-\TODO{add a high level description of the new strategy, discuss
-  decidability/approximation of the SAT checking, express some
-  ``minimality'' property}
-
-The basic algorithm from the previous section potentialy explores some
-areas of the global state-space that will not be reachable after
-checking the OTs' predicates for satisfiability. Incorporating the
-satisfiability check inside the residual algorithm will definitely
-save some of these useless computation. More precisely, it will still
-create, and submit to Z3, the OTs at the ``border'' of the state-space, but
-not the transitions issued from non-reachable global states.
-
-\ERIC{But there is more to this. As mentionned above, we collect all
-possible (symbolic) assignments of state variables, in the
-computed open automaton. By avoiding building the OTs coming from
-unreachable states, we also avoid adding the corresponding assignments
-to the variables of their target states. The set of possible
-assignments is an over approximation of possible values of the
-variables of such state, so narrowing it means we get a better
-approximation, and potentialy more informations, that can be used to
-the SAT check of subsequent transitions.}
-\TODO{Beware, I think this is dangerous... Xudong, do we really use
-  assignment information in SAT checking ? In the ``smart'' version, I
-  think we must NOT use it, because we do not yet have collected all
-  possible assignments.}
-
-Algorithm~\ref{alg3} implement this new stategy: \TODO{Explain
-  significant detials}
-
-\begin{algorithm}[h]
-  \caption{``Smart'' Reachable Open Automaton Generation}
-  \label{alg3}
-\begin{algorithmic}[1]
-\Require A pNet $P$ (cannot be a hole)
-        %\qquad \hl{\textbackslash\textbackslash~SB: was `` pn ''}
-\State Initialize sets $U=\{\mathit{InitState}(P)\}$ and $E=\emptyset$,
-for unexplored and explored global states, respectively; $L=\emptyset$ for the resulting OTs;
-\While{!$\mathit{isEmpty}(U)$}
-	\State Choose $S$ in $U$; remove $S$ from $U$, add $S$ to $E$;
-        %\qquad \hl{\textbackslash\textbackslash~SB: was `` Choose $S$ in $U$ ''}
-	\State $\mathit{OTs} = \mathit{MakeTransitions}(P, S)$;
-%%        \State Store $\mathit{OT}$ in $L$; 
-	\For {each $\mathit{OT} \in \mathit{OTs}$}
-        Check satisfiability of $\mathit{OT}$ using the SMT solver;
-        \IfThen {$SAT(\mathit{OT})$}
-                {\State \{Add $\mathit{OT}$ to $L$;
-                  \State Let $S'$ be the target global state of $\mathit{OT}$
-	          \IfThen{($S' \not\in U \cup E$)}{Add $S'$ into $U$;}
-                  \}}
-	\EndFor
-\EndWhile
-%%\State Prune the unsatisfiable open transitions in $L$ using the SMT solver;
-\State \Return $\mathit{OA}=(\mathit{InitState}(P),L)$;
-
-\end{algorithmic}  
-\end{algorithm}
-
-\TODO{Candidate theorems:
-  - All reachable states from algorithm 1 are kept by Algorithm 3\\
-  - Algorithm 3 computes an open automaton that is minimal with
-  respect of SAT checking decidability.\\
-  Of course we have to define this notion of minimality, that may be a
-  little tricky}
-
-\subsection{Translation to SMTlib}
-
-We check the satisfiability of each open transitions
-using the SMT solver Z3.
-%More precisely, we translate
-%the OT predicate into an SMTlib assertion in the context provided by
-%the possible state variable assignments in the source state.
-In this
-section, we describe the translation of the algebra presentation, of
-assignments, and of the predicates.
-
-Our implementation submits satisfiability requests to
-Z3 using its JAVA API. Here, for readability, we
-show the Z3 code using its SMT-LIB input language.
-Note that in the previous sections, the OTs were displayed in a
-  simplified, human readable form. The input and output of our tool, and
-  also the generated SMTlib fragments, are
-  slightly more difficult to read, in 
-particular because of structured names for the fresh variables generated
-by the algorithm, allowing tracability of the result~\cite{Avocs-RR}.
-
-Figure~\ref{schema:smt-lib} shows the translation of the
-transition of Fig.~\ref{schema:unsat-ot}
-in the SMTlib syntax.
-It contains the declaration
-of the BIP action algebra sorts 
-and constructors, then the declaration of variables, and finally the
-predicate to be checked, encoded as a set of assertions.
-Here the behavior of the hole ``B'' appears as a variable
-``|hb\_B:13:1|'', and line 10 shows the constraint that matching with
-a synchronisation vector has imposed on the behavior of ``B''.
-Here we display also the diagnosis (``sat'' or ``unsat'') generated by Z3.
-
-\begin{figure}[t]
-  %  \centerline{\includegraphics[width=12cm]{XFIG/SMTLIB2}}
-    \centerline{\includegraphics[width=\linewidth]{XFIG/SMTLIB3}}
-  \caption{The input of the Z3 solver in SMT-LIB language and the output result}  \label{schema:smt-lib}
-\end{figure}
-
-By lack of space, we have only shown here a use-case with boolean data
-parameters, so we only require the basic SAT capability of the Z3
-engine. It should be clear that more involved examples will require
-reasonning on predicates of various data types. Z3 provides theories for reasonning
-on integers, bitstrings, enumerated types, arrays, etc.
-We also need to deal with some universal quantification on free
-variables occuring in the guards of synch vectors.
-For other data structures usual in such models, like records, or
-recursive structures, the user will have to develop its own theories.
-Decidability of these theories will condition the completeness of the
-satisfiability check, and the decidability of model-checking or
-bisimulation checking.
-
-%% \noteSB{I am not sure I understand the entire message of this phrase}\hl{though in practice our tool only needs the brute information ``sat''
-%% or ``unsat''.
-%% The result "unsat" in the output is just what we expected.
-%% If the result is ``sat'', and more details are needed, Z3 can exhibit a
-%% model (i.e. an instanciation of the variables) showing the satisfiability.
-% as appears in the ``unsat'' proof generated by Z3 in which ``\{= ?x66 ?x70\}'' is shown to be false (see Fig. \ref{schema:smt-lib})
-
-%% \begin{figure}[t]
-%%   \centerline{\includegraphics[width=10cm]{XFIG/Interaction}}
-%%   \caption{The architecture of the interaction between pNet API and Z3}  \label{schema:interaction}
-%% \end{figure}
-
-\paragraph{Production of the SMT-lib code}
-  To build the input submitted to Z3 for each OT,
-we translate the algebra presentation, the predicates and the
-variable assignments into Z3 (Java-API) calls.
-% The $presentation$ and the predicates are translated separately.
-
-\emph{Translation of action algebra presentation.}
-In~\cite{Avocs-RR}, we  define the translation of an algebra presentation into
-SMTlib declarations (\texttt{declare-datatypes} and
-\texttt{declare-fun}). We also formalize a condition of well-formedness of pNets ensures that the generated code is correct,
-and will not raise runtime errors in the SMT engine. Note that the
-\texttt{declare-datatypes} command comprises both the action
-constructors from table \ref{table:BIPalgebra} and also the constant action
-names from our example.
-Additionally, we will include axiomatisation of any required functions
-and predicates of the presentation data-types.
-
-%% \paragraph{Translating assignments into predicate terms.}
-%% State variable assignments that were collected during the open
-%% automaton are used when generating the SMTlib asserts (see
-%% App.~\ref{appendix:translating-assignments}). \noteSB{I am not an expert of Z3 or SMT-LIB, but the clause '\texttt{(= t (- t 1))}' looks very suspicious to me.}\hl{This appears in
-%% line 10 of Fig.~\ref{schema:smt-lib}, which encodes possible values of
-%% the variable $t$ of the timer.}
-
-%The assignments are also taken into account when checking the
-%satisfiability of the open transitions as they represent the value of
-%the variables involved in an OT. In order to do that, we employs a
-%translation from assignments into term of predicates. The assignments
-%required to be translated are only those belong to the variables
-%contain in the start states of the open transitions. The assignments
-%are represented as equations between the variables and the expressions
-%on the right side of assignment. For the assignments of the same
-%variable, we do not figure out which state is the precursor of current
-%state, we keep all these possible equations instead, and generate the
-%disjunction of these equations. The state could always move to the
-%target state if there exists one of the values of its variable
-%satisfies the guard.
-%%\TODO{It won't matter the variable of the next state
-%%except that the right hand side expression contain its variables. This
-%%is a problem left to be solved in our future work. WHICH PROBLEM ?}
-%After that, for the assignments of the different variables, we generate a conjunction of them. This way we obtain a new term of the predicate involving assignments of the variables.
-
-%% State-variable assignments are also treated as a part of the
-%% predicates when checking the satisfiability. % Here we need conduct some
-%% % translations,
-%% For each assignement in a $\Post$ predicate, such as $\{s_0 \leftarrow 1\}$ in section
-%% ~\ref{section:op-semantics}, we translate it into an equation
-%% $s_0=1$. For several assignments of the same variable in the same state,
-%% we generate the disjunction of 
-%% these equations. Correspondingly, we generate a conjunction for the
-%% assignments from different variables.
-
-\emph{Translation of open transitions.}
-In~\cite{Avocs-RR} we formally define all steps of the translation of each
-open transition, including:
-%
-\begin{itemize}
-\item collect all variables in the transition, and declare them (using \texttt{declare-const})
-\item check well-formedness and correct typing of expressions,
-\item translate the predicate into a conjunction of assertions,
-\item if present in the source state, translate the state-variable
-  assignments into a disjunctive assertion.
-\end{itemize}
-%
-This translation ensures that no runtime error will occur
-in the SMT engine.
-
-Figure~\ref{schema:smt-lib} shows the decomposition of the
-predicate into a set of asserts, each encoding an elementary equality,
-inequality, or a guard. 
-The result (sat or unsat) of the final \texttt{check-sat} command in
-the translation () is then decoded.
-
-\section{Use-cases}
-\TODO{new section here, showing various features on different examples.
-Possible: Enable operator in Lotos, with (equivalent) state-based and data-based encodings; Associativity of Enable; simple communication protocol, specification and implementation; BIP FailureTimer architecture, including non-trivial ``Interval'' data-type and operators; without and with encoding of maximal progress.}
-
-\subsection{Result for the running example}
-\label{section:resultOA}
-\TODO{This is the original example from the Avocs paper}
+\paragraph{Variations on the FailureTimer example}
+
+\TODO{This is the original example from the Avocs paper, connectors slightly adapted so that it can be composed. Then Max Progress may be required to ensure properties}
+
 For this example, the tool builds 184 open transitions, whereof 173
@@
 
-%% \TODO{it would be good to express here maybe 2 properties of the
-%%   architecture, maybe one taken from the original study, and another
-%%   one involving the timer data (number of ticks ?)}
-
-\subsection{Extended version of the FailureTimer BIP Architecture}
-\label{section:resultTimerInterval}
-\TODO{Here we have extended the FailureTimer architecture using time intervals,
-  that makes more interesting the timeout/reset temporal behavior}
-
-We present here an extended version of the FailureTimer BIP
-architecture, in which the timeout action can occur
-non-deterministicaly during some time interval. This behavior is more
-realistic, but ensuring safety is a bit more complicated, as it
-involves reasonning on the time intervals in the predicates of the
-open automaton.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=0.9\columnwidth]{XFIG/BIPspec-ArchFailureTimerMax-v4}
-  \caption{The BIP specification of the Failure Monitor architecture}
-  \label{fig:schema:ArchFailure:BIP}
-\end{figure}
-
-Figure \ref{fig:schema:ArchFailure:BIP} shows components
-$\NameTimer$(imer) and $\NameCtrl$(ontrol), with interfaces
-$\btuple{
-  \{t, z\},
-  \{\PortTick, \PortCancel, \PortTOT\},
-  \bigl\{\!\PortTick \mapsto \{t, z\}\!\bigr\}
-}$,
-and
-$\btuple{
-  \{\mathit{zone}\},
-  \{\PortReset, \PortFail, \PortResume, \PortTOC\},
-  \bigl\{\!\PortFail \mapsto \{\mathit{zone}\}\!\bigr\}
-}$
-respectively.
-Variable $t$ is implicitly assumed to be an integer.  Variables $z$
-and $\mathit{zone}$ are  integer intervals of
-the form $[l,u]$.
-
-\TODO{refer to Research Report (not yet avaialble) or add an appendix,
-  for a full explanation of this example, 
-  and the translation from BIP to pNets}
-
 The safety
@@
 
-Figure \ref{fig:FailureTimer:pNet} shows the encoding of the Failure Monitor
-architecture, including the encodings of the two coordinators, \ie
-$\nopri[\NameTimer]$ and $\nopri[\NameCtrl]$.
+%% \TODO{it would be good to express here maybe 2 properties of the
+%%   architecture, maybe one taken from the original study, and another
+%%   one involving the timer data (number of ticks ?)}
+
+\subsection{Composing 2 FailureTimer BIP Architecture}
+\label{section:resultTimerInterval}
+\TODO{Enhanced FailureTimer, 2 instances composed, with duplicated control and Timer}
 

### 2019-03-14 2017-Xudong-SMT/ActaInformatica.tex
nouveau repertoire ACtaXFIG premiere version Timer-v2 inseree en pages 15-17

@@
 
-\TODO{use a simpler running example (e.g. Lotos Enable operator ?), and move the BIP example to a dedicated section at the end}
-
 As a running example we use the Failure Monitor architecture from the
@@
 each property, a corresponding architecture is identified
-%\,\footnote{%
-%
-%  The current approach relies on taxonomies of predefined
-%  architectures.  Future work may include automatic synthesis of
-%  architectures from, \eg CTL~\cite{BaierKatoen2008} formulae.
-%
-  %}
 and applied to the model, thereby potentially introducing additional
@@
   \centering
-  \includegraphics[width=0.8\columnwidth]{XFIG/BIPspec-ArchFailureTimerMax-v2}
+  \includegraphics[width=\columnwidth]{ActaXFIG/BIPspec-ArchFailureTimer-v2-1a}
   \caption{The BIP specification of the Failure Monitor architecture}
@@
 given.  Here, the operand component is $\NameOprnd$ and its interface
-consists of the ports $\PortFinish$, $\PortResume$ and $\PortFail$.
+consists of the ports $\PortResume$ and $\PortFail$.
 The two \emph{coordinator} components\mdash $\NameCtrl$ and
@@
 functions on local variables.  For instance the loop transition
-$\tstate{1} \goesto{\PortTick, \GuardTick[], \TimerUpd[]} \tstate{1}$
+$t_1 \goesto{\PortTick, [t < Max], t:=t+1} t_1$
 in the $\NameTimer$ component is labeled by the port $\PortTick$, it
 can be fired only when the current value of the local variable $t$ is
-greater than $0$.  Upon firing, this transition decrements the value
+lower than $Max$.  Upon firing, this transition increments the value
 of $t$ by $1$.  When omitted, the default guard (\resp update
 function) is the constant predicate $\true$ (\resp the $\mathit{skip}$
-operator).  The constant $\mathrm{Max}$, in $\tstate{0}
-\goesto{\PortStart, \TimerInit[]} \tstate{1}$, is a parameter of the
+operator).  The constant $\mathrm{Max}$ above, is a parameter of the
 architecture.
@@
 %
-For instance, the two ports $\NameTimer.\PortStart$ and
+For instance, the two ports $\NameTimer.start$ and
 $\NameCtrl.\PortFail$ are always synchronised, since they belong to
 the same binary sub-connector, where they are both synchrons.  In
-particular, this means that whenever the transition $\cstate{0}
-\goesto{\PortFail} \cstate{1}$ is fired, so is the transition
-$\tstate{0} \goesto{\PortStart, \TimerInit[]} \tstate{1}$,
+particular, this means that whenever the transition 
+$c_0 \goesto{\PortFail} c_1$ is fired, so is the transition
+$t_0 \goesto{\PortStart, t:=0} t_1$,
 initialising the timer.  The binary connector $\NameTimer.\PortStart
@@
 
-Finally, \emph{priorities}\mdash defined by a strict partial order on
-the set of possible interactions\mdash narrow the choice among the
-enabled interactions at any given round.  The default priority is the
-so-called \emph{maximal progress}, whereby among any two interactions
-$a \subset b$ (as sets of ports), $b$ has higher priority than $a$.
-For example, the port $\NameOprnd.\PortFail$ will never fire alone in
-a global state, where both $\NameTimer.\PortStart$ and
-$\NameCtrl.\PortFail$ are enabled.
+%% Finally, \emph{priorities}\mdash defined by a strict partial order on
+%% the set of possible interactions\mdash narrow the choice among the
+%% enabled interactions at any given round.  The default priority is the
+%% so-called \emph{maximal progress}, whereby among any two interactions
+%% $a \subset b$ (as sets of ports), $b$ has higher priority than $a$.
+%% For example, the port $\NameOprnd.\PortFail$ will never fire alone in
+%% a global state, where both $\NameTimer.\PortStart$ and
+%% $\NameCtrl.\PortFail$ are enabled.
+
 %
@@
   \centering
-  \includegraphics[width=0.9\columnwidth]{XFIG/FailureTimerPNET}
+  \includegraphics[width=0.9\columnwidth]{ActaXFIG/FailureTimerPNET-v2-1a}
   \caption{pNet encoding of the Failure Monitor architecture}
@@
 value to each of these ports: the original transitions carry the value
-$\true$ (\eg $\cstate{0} \goesto{\PortFail(\true)} \cstate{1}$), the
-added loops carry the value $\false$ (\eg $\cstate{2}
-\goesto{\PortFail(\false)} \cstate{2}$), 3)~add to the corresponding
+$\true$ (\eg $c_0 \goesto{\PortFail(\true)} c_1$), the
+added loops carry the value $\false$ (\eg $c_2
+\goesto{\PortFail(\false)} c_2$), 3)~add to the corresponding
 synchronisation vectors the Boolean predicate encoding the connector
@@
 %
-Although, for the sake of brevity, we omit priorities from the
+\noteEM{Decide later if this is still useful}Although, for the sake of brevity, we omit priorities from the
 encoding, this can be easily achieved, by introducing additional
@@
 
-\paragraph{Variations on the FailureTimer example}
-
-\TODO{This is the original example from the Avocs paper, connectors slightly adapted so that it can be composed. Then Max Progress may be required to ensure properties}
-
-For this example, the tool builds 184 open transitions, whereof 173
+\paragraph{Computed open automaton}
+
+For this example, the tool (using Algorithm 1) builds 218 open transitions, whereof 206
 are detected unsatisfiable by Z3.  The resulting open automaton, with
-3 reachable global states (out of the possible 6) and 11 open
-transitions, is shown in Fig.~\ref{schema:resultOA}.
+4 reachable global states (out of the possible 6) and 12 open
+transitions, is shown in Fig.~\ref{schema:resultOA1}.
 
 \begin{figure}[t]
-  \centerline{\includegraphics[width=12cm]{XFIG/FailureTimerOA}}
+  \centerline{\includegraphics[width=12cm]{ActaXFIG/FailureTimerOA-v2-1a}}
   \caption{Open Automaton for the Failure Monitor architecture}
-  \label{schema:resultOA}
+  \label{schema:resultOA1}
 \end{figure}
 
-To improve the readability of this figure, we used the following conventions:
-we omit the transitions of the two pLTS, and the set of ``working''
-holes; and we directly write the resulting action as first element of
-each OT, rather than including it as an equality inside the
-predicate.
+%% To improve the readability of this figure, we used the following conventions:
+%% we omit the transitions of the two pLTS, and the set of ``working''
+%% holes; and we directly write the resulting action as first element of
+%% each OT, rather than including it as an equality inside the
+%% predicate.
 %
@@
 \subsection{Composing 2 FailureTimer BIP Architecture}
+\noteInEM{Modifications stopped here}
 \label{section:resultTimerInterval}

### 2019-03-16 2019-ActaInformatica/ActaInformatica.tex
changes in writing

--- 2019-03-13 2017-Xudong-SMT/ActaInformatica.tex
@@
 
-\input{XFIG/macros.tex}         % Definitions of macros used in XFig figures
+\input{figures/macros.tex}         % Definitions of macros used in XFig figures
 \usepackage{macrospNets}
@@
 
-\title{Using an SMT engine to generate Symbolic Automata%
+\title{SMT-Based Generation of Symbolic Automata%
 %
@@
 \abstract{Open pNets are used to model the behaviour of open systems, both
-synchronous or asynchronous, expressed in various calculi or
+synchronous and asynchronous, expressed in various process calculi or
 languages. They are endowed with a symbolic operational semantics in
-terms of so-called ``Open Automata''. This allows us to check properties of
+terms of open automata, which allows us to check properties of
 such systems in a compositional manner. 
@@
 between the events of the pNet sub-systems. Checking such
-predicates requires symbolic reasoning over first order logics, but
-also over application-specific data. We use the Z3 SMT engine to check
-satisfiability of the predicates, and prune the open automaton of its
-unsatisfiable transitions.
-As an industrial oriented use-case, we use so-called ``architectures''
-for BIP systems, that have been used in the framework of an ESA project and to specify the control software of
-a nanosatellite at the EPFL Space Engineering Center. We use pNets to encode a BIP architecture
+predicates requires symbolic reasoning about first order logics and application-specific data. We use the Z3 SMT engine to check
+satisfiability of the predicates.
+%As an industrial oriented use-case, %we use so-called ``architectures''
+%for BIP systems, that have been used in the framework of an ESA project and to specify the control software of a nanosatellite at the EPFL Space Engineering Center. 
+As a use-case, we use pNets to encode a BIP architecture
 extended with explicit data, and compute its
 open automaton semantics. This automaton may be used to prove
-behavioural properties; we give 2 examples, a safety and a liveness
-property.
+behavioural properties such as safety and liveness.
 \TODO{Add new contrib}
 \todoMargin{Should we remove Min ?}
-\keywords{Networks of Synchronised Automata, Symbolic Behavioral Semantics, Compositional Analysis of Software Components, SMT}
+\keywords{pNets, software components, symbolic semantics, SMT}
 }
@@
 works extended the basic behavioural models based on labelled
-transition systems to address value-passing or parameterized systems, using
+transition systems to formalize value-passing or parameterized systems, using
 various symbolic encodings of the
 transitions~\cite{deSimone85,Larsen87,HennessyLin:TCS95,Linconcur96}. 
-In \cite{Linconcur96}, H.M. Lin addressed value-passing calculi, for which he
+In \cite{Linconcur96}, Lin considered value-passing calculi, for which he
 developed a symbolic behavioural semantics, and proved algebraic properties.
-Separately J. Rathke~\cite{HennessyRathke:TCS98} defined another
+Separately, Rathke~\cite{HennessyRathke:TCS98} defined another
 symbolic semantics for 
@@
 method for these processes. Thirty years later, no
-practical verification approach and no verification platform are
-using this kind of approaches to provide proof methods for
+practical verification approach and no verification platform use this kind of approaches to provide proof methods for
 value-passing processes or open process expressions.
@@
 is made of a hierarchical composition of (value-passing) automata,
-called parameterized labelled transition systems (pLTS), where each
+called parameterized labelled transition systems (PLTS), where each
 hierarchical level defines the possible synchronization of the lower levels.
@@
 other algebras or  program skeletons.
-The operational semantics of an (open) pNet is defined as an
-Open Automaton in which Open Transitions contain logical predicates
+The operational semantics of an open pNet is defined as an
+open automaton in which open transitions contain logical predicates
 expressing the relations between the behaviour of the holes, and the
@@
   \item to get a tool that could be applied to pNets representing
-    various languages, in particular various actions algebras,
+    various languages, in particular various action algebras,
     with their specific decision theories,
@@
 
-In the long term, we want to be able to check the equivalence between
+In the long term, we would like to check the equivalence between
 open systems encoded as pNets. The equivalence between pNets is
@@
 \paragraph{Contribution}
-In the article we show how:
+In the current work we contribute in the following aspects.
 \begin{itemize}
-\item We define the open automaton generation algorithm. We
-  implemented a full working prototype, within the 
-  VerCors platform. In the process, we improved the
+\item We present an open automaton generation algorithm. We
+  implement a full working prototype, within the 
+  VerCors platform. In the process, we improve the
   semantics rules from~\cite{henrio:Forte2016}, and add features in
@@
     generated by the algorithm.
-    \item \ERIC{we define a strategy checking satisfiability of open transitions in the course the residual algorithm, and show that this ensures that we still generate the reachable part of the open automaton, and that what is generated is minimal with respect to the decidability of predicate satisfiability}
-\item We show the interest of this approach \ERIC{on various use-cases from different settings}, including an
+    \item We define a strategy checking satisfiability of open transitions in the course of the residual algorithm, and show that  the reachable part of the open automaton can be generated and it is minimal with respect to the decidability of predicate satisfiability.
+\item We show the usage of this approach on various use-cases from different settings, including an
     industry-inspired case-study, namely one architectural pattern
@@
 interacting with automatic theorem provers. The closest work is the
-one already mentioned from J. Rathke~\cite{HennessyRathke:TCS98},
+one already mentioned by Rathke~\cite{HennessyRathke:TCS98},
 who developed the symbolic bisimulation for a
-calculus of broadcasting system (CBS). CBS is similar with classic
+calculus of broadcasting system (CBS). CBS is similar to classic
 process calculi such as CCS and CSP, but communicating by broadcasting
@@
 transmitting values without blocking. That makes the definition of
-the symbolic semantic and bisimulation equivalence different from the
+the symbolic semantics and bisimulation equivalence different from the
 classic works.
@@
 based on the satisfiability modulo 
-theories framework (SMT), is mainly applied in extended static checking, test case
+theories framework (SMT), and is mainly applied in extended static checking, test case
 generation, and predicate abstraction.
@@
 \paragraph{Structure.}
-In section
+In Section
 \ref{section:pnets} we give a description and a formal definition of
-the pNet model, as found in previous publications. Then in section
-\ref{section:examples} we present our use-case, based on a BIP
+the pNet model. In section
+In Section \ref{section:op-semantics} we briefly recall  the operational semantics
+of pNets.
+In Section \ref{section:implementation} we present an algorithm to compute this semantics, including the interaction with Z3.
+In Section~\ref{section:examples} we give a few use-cases, in particular, a BIP
 architecture from the nano-satellite case-study. 
-Section \ref{section:op-semantics} recalls briefly the operational semantics
-of pNet.
-Section \ref{section:implementation} explains in details the algorithm
-used to compute this semantics, including the interaction with Z3, and
-shows the full result of the semantic computation on the running example.
 Finally we conclude and discuss perspectives in Section
@@
 
-This section introduces pNets and the notations we will use in
-this paper. Then it gives the formal definition of pNet structures,
-together with an operational semantics for open pNets.
+We first introduce pNets and some notations. Then we give the formal definition of pNet structures, together with an operational semantics for open pNets.
 
 pNets are tree-like structures, where the leaves are either
-\emph{parameterized labelled transition systems (pLTSs)}, expressing the
+\emph{parameterized labelled transition systems (PLTSs)}, expressing the
 behaviour of basic processes, or \emph{holes}, used as placeholders
@@
 %\smallskip\noindent
-\paragraph*{Notations.}
+\paragraph*{Notations.} \
 We extensively use indexed structures
@@
 %follows:
-$a_i^{i\in I}$
+The symbole $a_i^{i\in I}$
 denotes a family of elements $a_i$ indexed over the
 set $I$.
-When this is not
-ambiguous, we shall use notations for sets, and typically write
-``indexed set over I'' when formally we should speak of multisets, and
+When this is unambiguous, we shall use notations for sets, and typically write
+``indexed set over I'' which formally means multisets, and
 write $x\in a_i^{i\in I}$ to mean $\exists i\in I.\, x=a_i$.  An empty
@@
 
-\paragraph*{Term algebra.}
+\paragraph*{Term algebra.} \
 Our models rely on a notion of parameterized actions that are
@@
 
-A pLTS is a labelled transition system with variables, which can be
+A PLTS is a labelled transition system with variables, which can be
 manipulated, defined, or accessed inside states, actions, guards, and
@@
 which can only be modified by the assignment in transitions targeting this state. 
-A global state variable of a pLTS is a state variable defined in all states.
+A global state variable of a PLTS is a state variable defined in all states.
 % $x$ satisfying $\forall s\!\in\! S .\, x\!\in\! \vars(s)$. 
@@
 
-We first define the set of actions a pLTS can use.  Let $a$
+We first define the set of actions a PLTS can use.  Let $a$
 range over action labels, $\symb{op}$ are operators, and $x_i$ range over
@@
 
-\begin{definition}[pLTS]
-\label{pLTS}
+\begin{definition}[PLTS]
+\label{PLTS}
 %\noteSB{It's a bit strange that algebra presentations are not referred to here}
-Given a term algebra $\Talg$, a pLTS is a tuple
-$pLTS\triangleq\mylangle S,s_0, \to\myrangle$ where:
+Given a term algebra $\Talg$, a PLTS is a tuple
+$PLTS\triangleq\mylangle S,s_0, \to\myrangle$ where:
 \begin{itemize}
@@
 pNet nodes as constructors for hierarchical structures.
-A pNet node has a set of sub-pNets that can be either pNets or pLTSs, and a
+A pNet node has a set of sub-pNets that can be either pNets or PLTSs, and a
 set of \emph{holes}, playing the role of process parameters
@@
 %% \begin{definition}[pNets]\label{def-pnets}
-%% A pNet is a hierarchical structure, whereof the leaves are pLTSs and holes:
-%% $\pNet::= pLTS~|~\mylangle \pNet_i^{i\in I}, S_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle$,
+%% A pNet is a hierarchical structure, whereof the leaves are PLTSs and holes:
+%% $\pNet::= PLTS~|~\mylangle \pNet_i^{i\in I}, S_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle$,
 %% where
@@
 %%     set of actions of a Hole  
-%%   or pNet), and also of $Leaves$ and $Holes$ (respectively all pLTSs
+%%   or pNet), and also of $Leaves$ and $Holes$ (respectively all PLTSs
 %%   and all holes in a pNet), can be found in \cite{henrio:Forte2016}.}
@@
   \begin{definition}[pNets]\label{def-pnets}
-    A pNet is a hierarchical structure where leaves are pLTSs and holes:
+    A pNet is a hierarchical structure where leaves are PLTSs and holes:
    %%  \footnote{Typing can 
@@
 %% sort~\cite{HMZ-FORTE2016}}
-$\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, J, \symb{SV}_k^{k\in 
+$\pNet\triangleq PLTS~|~\mylangle \pNet_i^{i\in I}, J, \symb{SV}_k^{k\in 
 K}\myrangle$, with $I, J, K$ potentialy infinite,
@@
 
-In Fig.~\ref{schema:EnableEncodings}, we show examples of these
-constructs, with two pLTSs, one hole and one pNet node encoding our running example.
+In Figure~\ref{schema:EnableEncodings}, we show examples of these
+constructs, with two PLTSs, one hole and one pNet node encoding our running example.
 
@@
 of several
-% \noteSB{These should all be pLTSs, right? Or did I miss
+% \noteSB{These should all be PLTSs, right? Or did I miss
 %  something?}\noteEM{Hum, nor really, something intermediate; the actions there can be
@@
 incoming transitions. Strictly speaking, the LTSs at the leaves of the
-open automaton are a restricted form of pLTSs, where labels are
+open automaton are a restricted form of PLTSs, where labels are
 parametrised actions, but include no guard nor assignments.
@@
 %transitions}, where the hypotheses on process parameters are
-%replaced by 1) transitions of the pLTSs at the leaves, and 2) formal
+%replaced by 1) transitions of the PLTSs at the leaves, and 2) formal
 %hypotheses on the transitions of the holes. A {\em predicate} is used
@@
   in structured states as $\triangleleft\ldots\triangleright$).
-  For any pNet p, let $\overline{\mathit{Leaves}} = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be the set of pLTS at its leaves,
+  For any pNet p, let $\overline{\mathit{Leaves}} = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be the set of PLTS at its leaves,
   then $\mathit{States}(p) = \{\ostate{s_i^{i\in L}}
   |\, \forall i\in L. s_i \in S_i\}$.
-A pLTS being its own single leave:
+A PLTS being its own single leave:
   $\mathit{States}(\mylangle S,s_0, \to\myrangle) = \{\ostate{s}|\, s \in S\}$.
@@
 \cite{henrio:Forte2016}, in the form of 2 structural rules, one for
-pLTSs, one for pNet nodes. These rules are slightly improved, adding guards in the synchronisation vectors and syntax for universal quantifier in the guards (see~\cite{Avocs-RR}).
+PLTSs, one for pNet nodes. These rules are slightly improved, adding guards in the synchronisation vectors and syntax for universal quantifier in the guards (see~\cite{Avocs-RR}).
 
@@
   \label{Th:finiteness}
-  Given an open pNet $pnet=\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $l_i^{i\in I}$ and holes $h_j^{j\in
-  J}$, if the sets $I$ and $J$ are finite, if the synchronisation vectors of all pNets 
-  included in  $pnet$   are finite, and if
-$\forall i \in L.\, finite{(states(l_i))} \text{ and } l_i$
-has a finite number of state variables, then its semantics is an open automaton 
-$\mathcal{T}$ with finitely many states and transitions.
+  Let $pnet=\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ be an open pNet  with leaves $l_i^{i\in I}$ and holes $h_j^{j\in
+  J}$, where the sets $I$ and $J$ are finite. Suppose the synchronisation vectors of all pNets 
+  included in  $pnet$   are finite, and 
+% $\forall i \in L.\, finite{(states(l_i))} \text{ and } l_i$ 
+$l_i $ has a finite number of state variables for each $i\in I$, then the semantics of $pnet$ is an open automaton 
+%$\mathcal{T}$ 
+with finitely many states and transitions.
 \end{theorem}
@@
   The possible set of states of the open-automaton is the cartesian
-  product of the states of its leaves $pLTS_i^{i\in L}$, that is finite by
+  product of the states of its leaves $PLTS_i^{i\in L}$, that is finite by
   hypothesis. So the top-level residual loop of Algorithm 1 terminates provided each 
@@
   applied finitely if the number
-  of transitions of each pLTS is finite. So we get finitely many deduction trees, and
+  of transitions of each PLTS is finite. So we get finitely many deduction trees, and
   open-transitions which ensures that each internal loop of Algorithm 1 terminates.
@@
 \begin{algorithmic}[1]
-\Require A pNet $P$ (can be a pLTS, but not a hole)
+\Require A pNet $P$ (can be a PLTS, but not a hole)
         %\qquad \hl{\textbackslash\textbackslash~SB: was `` pn ''}
@@
           \State Add $\mathit{OT}$ to $L$;
-          \State Let $S'$ be the target state of $\mathit{OT}$
-          Add $S'$ to the unexplored states if necessary:
+          \State Let $S'$ be the target state of $\mathit{OT}$;
+          \State Add $S'$ to the unexplored states if necessary:
 	  \IfThen{($S' \not\in U \cup E$)}{Add $S'$ into $U$;}
@@
 the semantic rules following the structure of the pNet.
-When applied to a pLTSs at the leaves, we simply take the pLTS transitions of the
+When applied to a PLTSs at the leaves, we simply take the PLTS transitions of the
 corresponding local state and use the semantic rule to build the OT\footnote{%
@@
 %% \noteInSB{Algorithm~\ref{alg2}, as presented below is not
-%%   well-defined: when we reach the leaves, a pLTS does not have any
+%%   well-defined: when we reach the leaves, a PLTS does not have any
 %%   subnets, hence the loop in lines 2--4 is empty and so is the list
@@
 unification  will be checked later, together with the guards collected
-from synchronisation vectors and from pLTS transtions, using the
+from synchronisation vectors and from PLTS transtions, using the
 satisfiability check in the SMT engine.
@@
 
-In a pLTS, there may be several incoming transitions 
+In a PLTS, there may be several incoming transitions 
 that assign potentially different values to a state variable.
-To handle such cases, the algorithm manages, for each pLTS state, a
+To handle such cases, the algorithm manages, for each PLTS state, a
 list of expressions collected from the assignments of each state
@@
 %% The list we used contains triples <$v$, $S$, $AssignRH$> 
-%% where $v$ is the variable in pLTS, $S$ is its owner state and
+%% where $v$ is the variable in PLTS, $S$ is its owner state and
 %% $AssignRH$ is a list of expressions over other variables in the right
@@
 % As a pragmatic extension to the formal definition, we also manage
-% ``global variables'', defined in all states of the pLTS.
+% ``global variables'', defined in all states of the PLTS.
 For a global state in the open automaton, the set of state
@@
 is the disjoint union
-of sets of state variables of the individual pLTS states constituting this
+of sets of state variables of the individual PLTS states constituting this
 global state.
-%There are some assignment on the variables in each of states of the pLTS (state variables), or just as global states of it (global variables).
+%There are some assignment on the variables in each of states of the PLTS (state variables), or just as global states of it (global variables).
 There is usually not only one assignment for a state variable, miss of them may drop the unsatisfiable results.
@@
 %% The list we used contains several triples <$v$, $S$, $AssignRH$> to
-%% record the information of both state and global variables of the pLTS,
-%% where $v$ is the variable in pLTS, $S$ is its owner state and
+%% record the information of both state and global variables of the PLTS,
+%% where $v$ is the variable in PLTS, $S$ is its owner state and
 %% $AssignRH$ is a list of expressions over other variables in the right
 %% hand side of assignments of $v$. It means the variable is global in
-%% the pLTS belonging to all the states, if $S$ is $null$. We update the
+%% the PLTS belonging to all the states, if $S$ is $null$. We update the
 %% list of record triples every time Tr1 is applied. Then we can track
@@
 
-By lack of space, we have only shown here a use-case with boolean data
+For simplicity, we have only shown here a use-case with boolean data
 parameters, so we only require the basic SAT capability of the Z3
 engine. It should be clear that more involved examples will require
-reasonning on predicates of various data types. Z3 provides theories for reasonning
-on integers, bitstrings, enumerated types, arrays, etc.
+reasonning about predicates of various data types. Z3 provides theories for reasonning
+about integers, bitstrings, enumerated types, arrays, etc.
 We also need to deal with some universal quantification on free
-variables occuring in the guards of synch vectors.
-For other data structures usual in such models, like records, or
+variables occuring in the guards of synchronization vectors.
+For other data structures  in such models, like records, or
 recursive structures, the user will have to develop its own theories.
@@
 SMTlib declarations (\texttt{declare-datatypes} and
-\texttt{declare-fun}). We also formalize a condition of well-formedness of pNets ensures that the generated code is correct,
+\texttt{declare-fun}). We also formalize a condition of well-formedness of pNets to ensure that the generated code is correct,
 and will not raise runtime errors in the SMT engine. Note that the
 \texttt{declare-datatypes} command comprises both the action
-constructors from table \ref{table:BIPalgebra} and also the constant action
+constructors from Table~\ref{table:BIPalgebra} and also the constant action
 names from our example.
-Additionally, we will include axiomatisation of any required functions
+Additionally, we will include axiomatization of any required functions
 and predicates of the presentation data-types.
@@
 \begin{itemize}
-\item collect all variables in the transition, and declare them (using \texttt{declare-const})
-\item check well-formedness and correct typing of expressions,
-\item translate the predicate into a conjunction of assertions,
-\item if present in the source state, translate the state-variable
-  assignments into a disjunctive assertion.
+\item to collect all variables in the transition, and declare them (using \texttt{declare-const})
+\item to check the well-formedness and correct typing of expressions,
+\item to translate the predicate into a conjunction of assertions,
+\item to translate the state-variable
+  assignments into a disjunctive assertion, if the assignments are present in the source state.
 \end{itemize}
@@
 
-\section{Use-cases}
+\section{Use-cases}\label{sec:cases}
 \TODO{new section here, showing various features on different examples}
@@
 above Failure Monitor architecture.  This encoding is structural: each
-coordinator component is encoded as a pLTS, the operand
+coordinator component is encoded as a PLTS, the operand
 component\mdash as a hole; connectors of the BIP model are encoded as
@@
 the same ports.  In order to encode the semantics of the connectors
-involving triggers, we 1)~in the pLTS encoding the coordinator
+involving triggers, we 1)~in the PLTS encoding the coordinator
 components, add loop transitions to ensure that all ports involved in
@@
 To improve the readability of this figure, we used the following conventions:
-we omit the transitions of the two pLTS, and the set of ``working''
+we omit the transitions of the two PLTS, and the set of ``working''
 holes; and we directly write the resulting action as first element of
@@
 %App.~\ref{appendix:fullOutput}, involve $\OTvar{resume(false)}$ from
-%the two pLTS, \ie only the hole, corresponding to the operand
+%the two PLTS, \ie only the hole, corresponding to the operand
 %component of the Failure Monitor architecture, executes $\PortResume$.
@@
 We build the semantics of an open pNet as an open automaton where
-LTSs are the pLTSs at 
+LTSs are the PLTSs at 
 the pNet leaves, and the states are structured as in
@@
  projects the global state into states of the leaves, then applies
-pLTS transitions on these states, and compose them with actions of
+PLTS transitions on these states, and compose them with actions of
 holes using synchronisation vectors. %The pNet
@@
 Tr2). Similarly the state variables of each copy of a
-given pLTS in the system, must be distinct, and those created for each
+given PLTS in the system, must be distinct, and those created for each
 application of Tr2 have to be fresh and all distinct.
@@
 
-  The rule ({\bf Tr1}) for a pLTS $p$  checks that the guard 
+  The rule ({\bf Tr1}) for a PLTS $p$  checks that the guard 
   is verified and transforms assignments into post-conditions:
@@
 % each variables, and to introduce additional variables to handle the several occurence 
-% of the same pLTS variable in the predicates. Indeed the constraints on pLTS 
+% of the same PLTS variable in the predicates. Indeed the constraints on PLTS 
 % transitions 
@@
     \alpha'_k, G_k \\
-      Leaves(p) \!=\! \pLTS_l^{l\in L} \\     
+      Leaves(p) \!=\! \PLTS_l^{l\in L} \\     
       \forall m\in I_k.
@@
       %\land
-      %Leaves(\pNet_m) = \overline{pLTS}^{L_k})
+      %Leaves(\pNet_m) = \overline{PLTS}^{L_k})
       \\
@@
 with finite synchronization sets, finitely many leaves and
-holes, and each pLTS at leaves having a finite number of states and
+holes, and each PLTS at leaves having a finite number of states and
 (symbolic) transitions, has a finite automaton. The proof can be found
@@
 Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in
-    K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
+    K}\myrangle$ with leaves $PLTS_i^{i\in L}$ and holes $Hole_j^{j\in
   J}$,
@@
 occurrence of a vector (= each time we instantiate rule
-Tr2). Similarly the state variables of each copy of a given pLTS in
+Tr2). Similarly the state variables of each copy of a given PLTS in
 the system, must be distinct, and those created for each application
@@
 \label{appendix:translating-assignments}
-In a pLTS, there may be several incoming transitions 
+In a PLTS, there may be several incoming transitions 
 that assign potentially different values to a state variable.
-To handle such cases, the algorithm manages for each pLTS state, as a
+To handle such cases, the algorithm manages for each PLTS state, as a
 list of expressions collected from the assignments of each state
@@
 % As a pragmatic extension to the formal definition, we also manage
-% ``global variables'', defined in all states of the pLTS.
+% ``global variables'', defined in all states of the PLTS.
 For a global state in the open automaton, getting the set of state
 variables (which may be used in a transition) will simply be the union
-of state variables of the individual pLTS states constituting this
-global state, as variables of different pLTS are distinct.
+of state variables of the individual PLTS states constituting this
+global state, as variables of different PLTS are distinct.
 
@@
     (sorts and operators) that is defined for a given language (process calculus, or high level programming language),
-    \item for a given pNet, the set of local constants (actions or auxiliary data) that are used in the pLTSs,
+    \item for a given pNet, the set of local constants (actions or auxiliary data) that are used in the PLTSs,
     \item for each open transition: the declaration of variables, and
@@
 \begin{itemize}
-\item $Const(pnet)$: Constants from the pLTSs (controllers) transitions: these are
+\item $Const(pnet)$: Constants from the PLTSs (controllers) transitions: these are
   new constant constructors, usually of sort Action, local to an
@@
 all variables used in OT.
-\subitem check that all pLTS labels (action, guard, assignment) in
+\subitem check that all PLTS labels (action, guard, assignment) in
 the transition, the OT predicate, and the OT assignments are
@@
 use-case. It is displayed in full and raw format, each OT containing
-in its premisses: the list of transitions of pLTSs and actions of
+in its premisses: the list of transitions of PLTSs and actions of
 holes, the predicate, the Post assignements. In the conclusion the
@@
 When it comes to a pNet node, all the variables from the sources mentioned above should be contained in the $InterVar$ together with the intermediate variables from the subnets.
-Whatever its subnet is a pLTS or pNets.
+Whatever its subnet is a PLTS or pNets.
 At the same time, the subnet's result action should be add into the $InterVar$.

### 2019-03-16 2019-ActaInformatica/ActaInformatica.tex
minor changes

@@
 
-\abstract{Open pNets are used to model the behaviour of open systems, both
-synchronous and asynchronous, expressed in various process calculi or
-languages. They are endowed with a symbolic operational semantics in
+\abstract{Open pNets are formal models that can express the behaviour of open systems, either
+synchronous, asynchronous, or heterogeneous. They are endowed with a symbolic operational semantics in
 terms of open automata, which allows us to check properties of
 such systems in a compositional manner. 
-We implement an algorithm computing these semantics,
+We propose and implement an algorithm computing these semantics,
 building predicates expressing the synchronization conditions
@@
 %for BIP systems, that have been used in the framework of an ESA project and to specify the control software of a nanosatellite at the EPFL Space Engineering Center. 
-As a use-case, we use pNets to encode a BIP architecture
-extended with explicit data, and compute its
+We also present several use-cases, in particular, encoding a BIP architecture
+extended with explicit data and computing its
 open automaton semantics. This automaton may be used to prove
@@
 transitions~\cite{deSimone85,Larsen87,HennessyLin:TCS95,Linconcur96}. 
-In \cite{Linconcur96}, Lin considered value-passing calculi, for which he
-developed a symbolic behavioural semantics, and proved algebraic properties.
+In \cite{Linconcur96}, Lin considered value-passing CCS, for which he
+developed a symbolic behavioural semantics, and developed algorithms for checking symbolic bisimulations.
 Separately, Rathke~\cite{HennessyRathke:TCS98} defined another
@@
 equivalences, and developed a symbolic model-checker based on a tableau
-method for these processes. Thirty years later, no
-practical verification approach and no verification platform use this kind of approaches to provide proof methods for
+method for these processes. 
+Later on, symbolic semantics were extended to the $\pi$-calculus and decision algorithms for various symbolic bisimulations were proposed \cite{Li99,Deng2001}. However, no
+practical verification approach or  platform uses this kind of approaches to provide proof methods for
 value-passing processes or open process expressions.

### 2019-03-17 2019-ActaInformatica/ActaInformatica.tex
more changes

@@
 We propose and implement an algorithm computing these semantics,
-building predicates expressing the synchronization conditions
+building predicates expressing the synchronisation conditions
 between the events of the pNet sub-systems. Checking such
@@
 works extended the basic behavioural models based on labelled
-transition systems to formalize value-passing or parameterized systems, using
+transition systems to formalize value-passing or parameterised systems, using
 various symbolic encodings of the
@@
 symbolic semantics for 
-a parameterized broadcast calculus, together with strong and weak bisimulation
+a parameterised broadcast calculus, together with strong and weak bisimulation
 equivalences, and developed a symbolic model-checker based on a tableau
@@
 Later on, symbolic semantics were extended to the $\pi$-calculus and decision algorithms for various symbolic bisimulations were proposed \cite{Li99,Deng2001}. However, no
-practical verification approach or  platform uses this kind of approaches to provide proof methods for
+practical verification platform has been developed to use this kind of approaches to provide proof methods for
 value-passing processes or open process expressions.
 
-Parameterized Networks of Synchronized Automata (pNets) were proposed
+Parameterised Networks of synchronised Automata (pNets) were proposed
 to give a behavioural specification formalism for distributed
@@
 high-level languages. The high-level languages in VerCors formalize
-each component of the distributed system and their composition.
+each component of a distributed system and their composition.
 pNets provides the core low-level semantic formalism for VerCors, and
 is made of a hierarchical composition of (value-passing) automata,
-called parameterized labelled transition systems (PLTS), where each
-hierarchical level defines the possible synchronization of the lower levels.
+called parameterised labelled transition systems (PLTS), where each
+hierarchical level defines the possible synchronisation of the lower levels.
 Traditionally, pNets have been used to formalize fully
@@
 expressing the relations between the behaviour of the holes, and the
-global behaviour of the system. In the previous publication,
-only a sketch of a procedure allowing to compute these semantics was
+global behaviour of the system. In previous work,
+only a sketch of a procedure allowing for computing these semantics was
 presented, together with a proof of finiteness of the open automaton, under
@@
 \begin{itemize}
-  \item to get a tool that could be applied to pNets representing
+  \item to obtain a tool that could be applied to pNets representing
     various languages, in particular various action algebras,
-    with their specific decision theories,
+    with their specific decision theories;
   \item to separate clearly the 
       algorithm generating the transitions of the open automaton from
-      combination of all possible (symbolic) behaviours, from
+      combination of all possible (symbolic) behaviours, and from
       the symbolic reasoning part, specifically here using an SMT
       engine to check the
-      satisfiability of the predicates generated by our algorithm,
+      satisfiability of the predicates generated by our algorithm;
   \item to build a prototype and validate the approach on our basic
@@
 %% There is not much research work towards trying 
-Very few attempts were made to develop symbolic bisimulation approaches
-for the value-passing process algebras and languages\mdash our long-term goals\mdash
-especially, there is no algorithmic treatment of the symbolic systems developed by
+As mentioned above, early attempts were made by Lin and others to define symbolic bisimulations for process calculi such as value-passing CCS and the $\pi$-calculus, and design algorithms to compute the most general condition under which two processes are bisimilar.
+However, there is no algorithmic treatment of the symbolic systems developed by
 interacting with automatic theorem provers. The closest work is the
@@
 BIP
-(Behaviour-Interaction-Priority)~\cite{bip} is a framework for the
+(Behaviour-Interaction-Priority)~\cite{bip} is a framework for 
 component-based design of concurrent software and systems.  In
@@
 \ref{section:pnets} we give a description and a formal definition of
-the pNet model. In section
+the pNet model. 
 In Section \ref{section:op-semantics} we briefly recall  the operational semantics
@@
 
-We first introduce pNets and some notations. Then we give the formal definition of pNet structures, together with an operational semantics for open pNets.
+We first introduce pNets and some notations, then give the formal definition of pNet structures, together with an operational semantics for open pNets.
 
 pNets are tree-like structures, where the leaves are either
-\emph{parameterized labelled transition systems (PLTSs)}, expressing the
+\emph{parameterised labelled transition systems (PLTSs)}, expressing the
 behaviour of basic processes, or \emph{holes}, used as placeholders
@@
 actions, named \emph{sort}.
-Nodes of the tree (pNet nodes) are synchronizing artifacts, using a
-set of \emph{synchronization vectors} that express the possible
-synchronization between the parameterized actions of a subset of the
+Nodes of the tree (pNet nodes) are synchronising artifacts, using a
+set of \emph{synchronisation vectors} that express the possible
+synchronisation between the parameterised actions of a subset of the
 sub-trees.
@@
 ``indexed set over I'' which formally means multisets, and
-write $x\in a_i^{i\in I}$ to mean $\exists i\in I.\, x=a_i$.  An empty
-family is denoted $\emptyset$. We
+write $x\in a_i^{i\in I}$ to mean $x=a_i$ for some $i\in I$.  An empty
+family is written $\emptyset$. We
 denote classically $\overline{a}$ a family when the indexing set is
-irrelevant.  $\uplus$ is the disjoint union on indexed sets.
+irrelevant. The symbol $\uplus$ stands for the disjoint union of indexed sets.
 
 \paragraph*{Term algebra.} \
-Our models rely on a notion of parameterized actions that are
+Our models rely on a notion of parameterised actions that are
 symbolic expressions using data types and variables. As we want to encode
@@
 mechanism, based on unification between two or more action
-expressions. This will be used in the semantics of synchronization
-vectors to express various kinds of communication or synchronization mechanisms.
+expressions. This will be used in the semantics of synchronisation
+vectors to express various kinds of communication or synchronisation mechanisms.
 
@@
 
-\paragraph*{Algebra presentations.}
-In practice, the parameterization of the pNet model by some specific
-action algebra is realized by the definition of a many-sorted ``algebra
-presentation''. It will be used to check the
+\paragraph*{Algebra presentations.}\
+In practice, the parameterisation of the pNet model by some specific
+action algebra is realised by the definition of a many-sorted algebra
+presentation. It will be used to check the
 well-formedness of a pNet system, and to define the translation of the pNet
@@
   \begin{itemize}
-  \item $Sorts$ is a set of data \emph{sorts}
+  \item $Sorts$ is a set of data sorts.
     % \noteSB{Commented out a footnote here\mdash check if still necessary.}
@@
       arity and signature, of the form: $Op : \mathit{sort}_1, \dots,  \mathit{sort}_n \rightarrow
-      \mathit{sort}$
+      \mathit{sort}$.
       \item $\mathit{Constrs}(\mathit{sortname})$ and $\mathit{Sels}(\mathit{sortname})$ are, respectively, the sets of
-        constructors and selectors of the sort $\mathit{sortname}$
+        constructors and selectors of the sort $\mathit{sortname}$.
   \end{itemize}
@@
 Sorts \texttt{Bool} and \texttt{Int} are predefined with standard operators.
-Sort \texttt{Action} also, with a constructor \texttt{Synchro} denoting
-a synchronized action, i.e. an ``internal'' action that cannot be
-further synchronized with the environment. It also comes with an
+Sort \texttt{Action} is similar, with a constructor \texttt{Synchro} denoting
+a synchronised action, i.e. an ``internal'' action that cannot be
+further synchronised with the environment. It also comes with an
 overloaded \texttt{FUN} constructor, used to build actions with
-arguments, that will be instantiated to the required sorts for a given
+arguments, which will be instantiated to the required sorts for a given
 pNet.
 
-The definition of an Algebra Presentation, and a set of variables
-$\P$ fixes the Term algebra elements $\Talg, \AlgB_{\P}, \AlgA_\P$.
+The definition of an algebra presentation and a set of variables
+$\P$ fix the term algebra elements $\Talg, \AlgB_{\P}, \AlgA_\P$.
 
@@
 		\\\hline\specialrule{0em}{1pt}{1pt}
-\multicolumn{3}{l}{\sl Extension for the BIP use-case of Fig.~\ref{schema:ArchFailure:pNet}}
+\multicolumn{3}{l}{\sl Extension for the BIP use-case of Figure~\ref{schema:ArchFailure:pNet}}
 		\\\hline\specialrule{0em}{1pt}{1pt}
@@
 
-\subsection{The (open) pNets Core Model}
+\subsection{The (Open) pNets Core Model}
 \label{section:pNets}
@@
 $\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in J}\rangle$,
-  where $\alpha \in\AlgA_{\P}$ is a parameterized action,
+  where $\alpha \in\AlgA_{\P}$ is a parameterised action,
     $e_b \in \AlgB_{\P}$ is a guard, and
@@
 %% internal actions is
-are given by  \emph{synchronization vectors}, which %% : a
-%% synchronization vector 
-synchronize one or several internal actions, and
+are given by  \emph{synchronisation vectors}, which %% : a
+%% synchronisation vector 
+synchronise one or several internal actions, and
 expose a single resulting global action.
@@
 %% \item[$\bullet$] $\symb{SV}_k^{k\in K}$, with $K\in\I_\P$, is a set of
-%%   synchronization vectors: for each $k\!\in\! K$,
+%%   synchronisation vectors: for each $k\!\in\! K$,
 %%   $\symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k$ where
@@
 	here a simple example based on the ``Enable'' operator of the LOTOS language.
-	In Fig. \ref{schema:enable-pnets}, we show 2 possible encodings of the  
+	In Figure \ref{schema:enable-pnets}, we show 2 possible encodings of the  
 	``Enable'' operator.
@@
 	In the first encoding $Enable1$, in the upper part of
-	Fig. \ref{schema:enable-pnets}, we use a controller $C_1$ with two
+	Figure \ref{schema:enable-pnets}, we use a controller $C_1$ with two
 	states, and simple control actions $l, r, \delta$. The second encoding
@@
           actions}, to express actions that cannot be further synchronised, like the
-        $\tau$ silent action of CCS. We denote them as any action expression with the text
+         silent action $\tau$ of CCS. We denote them as any action expression with the text
         underlined, as e.g. $\underline{\delta(x_2)}$. Such
-        synchronised actions do not play any special role for defining
+         actions do not play any special role for defining
         the semantics of pNets, but as one can expect, will be crucial
@@
 
-	In Fig. \ref{schema:enable-composed}, we enrich our example by
-	composing 2 occurences of the Enable1 pNet. To simplify,
-	we only have represented one instance of the synchronisation vector set,
+	In Figure \ref{schema:enable-composed}, we enrich our example by
+	composing 2 occurences of the Enable1 pNet. For simplicity,
+	we only represent one instance of the synchronisation vector set,
 	and of the controller.
@@
 $\mylangle\overline{\pNet},J,\symb{SV}_k^{k\in K} \myrangle$
-be a pNet. Consider a synchronization vector $SV_k$, for $k\in K$. We build a
+be a pNet. Consider a synchronisation vector $SV_k$, for $k\in K$. We build a
 predicate $\MkPred$ relating
@@
 \paragraph{Structural Semantic Rules:}
-The semantics of pNet in term of open automata has been defined in
-\cite{henrio:Forte2016}, in the form of 2 structural rules, one for
+The semantics of pNets in term of open automata has been defined in
+\cite{henrio:Forte2016}, in the form of two structural rules, one for
 PLTSs, one for pNet nodes. These rules are slightly improved, adding guards in the synchronisation vectors and syntax for universal quantifier in the guards (see~\cite{Avocs-RR}).
@@
     behavior of matching/combining/filetring ?)}
-  The possible set of states of the open-automaton is the cartesian
+  The possible set of states of the open automaton is the cartesian
   product of the states of its leaves $PLTS_i^{i\in L}$, that is finite by
@@
 In this section we describe the algorithm implementing the pNet
-semantics, the interaction with the Z3 SMT solver, and we show the
-result on our example. Under the hypotheses of Theorem \ref{Th:finiteness}
+semantics and the interaction with the Z3 SMT solver. Under the hypotheses of Theorem \ref{Th:finiteness}
 this algorithm terminates.
@@
 transitions. Its main loop is a classical residual algorithm: starting
-from the initial global state, it picks a state in an unexplored set, and
-computes all possible OTs, adding their target states in the
+from the initial global state, it picks a state in an unexplored set, 
+computes all possible OTs, and adds the target states in the
 unexplored set, until this set is empty.
@@
 Here, we only detail the construction of the predicate.
-From a synchronization vector
-$sv = \left((a'_i)^{i\in I} (b'_j)^{j\in J}\rightarrow v'\right) \in SV$
-and its guard $G_k$; a tuple of open transitions
-$C = ({ot}_i)^{i \in [1,n]} \in \overline{comb}$, such that, for each $i \in [1,n]$, either $ot_i = -$, or the result action of $ot_i$ is $a_i$; the hole behaviours $\mathit{Hole} = (b_j)^{j \in J}$; and a fresh variable $v$, representing the result action of the OT under construction, we build the predicate:
+Suppose $sv = \left((a'_i)^{i\in I} (b'_j)^{j\in J}\rightarrow v'\right) \in SV$ is a synchronisation vector, $G_k$ is its guard, 
+$C = ({ot}_i)^{i \in [1,n]} \in \overline{comb}$ is a tuple of open transitions such that, for each $i \in [1,n]$, either $ot_i = -$, or the result action of $ot_i$ is $a_i$.
+Suppose futher that $\mathit{hole} = (b_j)^{j \in J}$ is the hole behaviour and $v$ is a fresh variable, representing the result action of the OT under construction.
+Then we can  build the predicate:
 %
@@
 apply only the simplest filter inside the \emph{Matching} method
-(before applying the predicate and OT construction). Matching and
+(before applying the predicate and the  OT construction). Matching and
 unification  will be checked later, together with the guards collected
@@
 we choose to minimize the open automaton (\ie its number of
-transitions and states), by checking the predicates for satisfiability.
-In Fig.~\ref{schema:unsat-ot}, we show an 
+transitions and states) by checking the predicates for satisfiability.
+In Figure~\ref{schema:unsat-ot}, we show an 
 unsatisfiable open transition 
@@
 the failure controller performs a ``$\PortFail$'' action, while the timer
-executes a ``$\PortResume$''. The chosen synchronization
-vector (SV0 from Fig.~\ref{schema:ArchFailure:pNet}) does not match
+executes a ``$\PortResume$''. The chosen synchronisation
+vector (SV0 from Figure~\ref{schema:ArchFailure:pNet}) does not match
 with these actions, since it expects $\NameTimer.\PortStart$. This
@@
 may depend on the specific theory of the action algebra datatypes. 
-The ``Modulo Theory'' part of SMT solvers is important here, so that
+The ``Modulo Theory'' part of SMT solvers is important here, as
 the solver can use specific properties of each action algebra.
@@
 
-The basic algorithm from the previous section potentialy explores some
+The basic algorithm from the previous section potentially explores some
 areas of the global state-space that will not be reachable after
@@
 Figure~\ref{schema:smt-lib} shows the translation of the
-transition of Fig.~\ref{schema:unsat-ot}
+transition of Figure~\ref{schema:unsat-ot}
 in the SMTlib syntax.
@@
 We also need to deal with some universal quantification on free
-variables occuring in the guards of synchronization vectors.
+variables occuring in the guards of synchronisation vectors.
 For other data structures  in such models, like records, or
@@
 %% App.~\ref{appendix:translating-assignments}). \noteSB{I am not an expert of Z3 or SMT-LIB, but the clause '\texttt{(= t (- t 1))}' looks very suspicious to me.}\hl{This appears in
-%% line 10 of Fig.~\ref{schema:smt-lib}, which encodes possible values of
+%% line 10 of Figure~\ref{schema:smt-lib}, which encodes possible values of
 %% the variable $t$ of the timer.}
@@
 the ports of the corresponding components, Boolean guards and update
-functions on local variables.  For instance the loop transition
+functions on local variables.  For instance, the loop transition
 $\tstate{1} \goesto{\PortTick, \GuardTick[], \TimerUpd[]} \tstate{1}$
-in the $\NameTimer$ component is labeled by the port $\PortTick$, it
+in the $\NameTimer$ component is labelled by the port $\PortTick$. It
 can be fired only when the current value of the local variable $t$ is
@@
 attributes of the connected ports~\cite{BliSif08-acp-tc}, which may be
-either \emph{trigger} (triangles in Fig.~\ref{schema:ArchFailure:BIP})
-or \emph{synchron} (bullets in Fig.~\ref{schema:ArchFailure:BIP}).
+either \emph{trigger} (triangles in Figure~\ref{schema:ArchFailure:BIP})
+or \emph{synchron} (bullets in Figure~\ref{schema:ArchFailure:BIP}).
 %
@@
 value to each of these ports: the original transitions carry the value
-$\true$ (\eg $\cstate{0} \goesto{\PortFail(\true)} \cstate{1}$), the
+$\true$ (\eg $\cstate{0} \goesto{\PortFail(\true)} \cstate{1}$) and the
 added loops carry the value $\false$ (\eg $\cstate{2}
@@
 3 reachable global states (out of the possible 6) and 11 open
-transitions, is shown in Fig.~\ref{schema:resultOA}.
+transitions, is shown in Figure~\ref{schema:resultOA}.
 
@@
 
-To improve the readability of this figure, we used the following conventions:
-we omit the transitions of the two PLTS, and the set of ``working''
-holes; and we directly write the resulting action as first element of
+To improve the readability of this figure, we use the following conventions:
+we omit the transitions of the two PLTSs, and the set of ``working''
+holes; and we directly write the resulting action as the first element of
 each OT, rather than including it as an equality inside the
@@
 %$\ostate{s2,t0}$, corresponding, respectively, to open transitions
-%$ot_2$ and $ot_9$ in Fig.~\ref{schema:ots} of
+%$ot_2$ and $ot_9$ in Figure~\ref{schema:ots} of
 %App.~\ref{appendix:fullOutput}, involve $\OTvar{resume(false)}$ from
@@
 Figure \ref{fig:ArchFailure:OA} shows the open automaton built by our
-algorithm. For reasons of readability, we did not show the full
+algorithm. For reasons of readability, we do not show the full
 details of the open transitions on this figure. Below we list the
-first 3 of them (full details available in \ref{TimerRR}). 
+first three of them (full details available in \ref{TimerRR}). 
 This automaton has 12 transitions, including those encoding various
-possible firing of some interactions (e.g. OT 2 and 3 for
-{\PortFail}). It looks like the rough behaviour is
+possible firing of some interactions (e.g. OTs 2 and 3 for
+{\PortFail}). It appears that the rough behaviour is
 reasonable, although a detailed study shows that the property stated
 above does not hold, because of the
-{\PortFail} loops on states $11$ and $12$. This is because we did not
+{\PortFail} loops on states $11$ and $12$. The reason is that we do not
 use the maximal progress assumption here. If we do, we get the
@@
 
-In each cell of the following table, we display the number of OTs whose predicates were founSAT/UNSAT by the SMT engine, and the overall time spent for the whole algorithm execution.
-
+In each cell of the following table, we display the number of OTs whose predicates were founSAT/UNSAT by the SMT engine, and the overall time spent for the execution of the whole algorithm.
+
+\medskip
 	\begin{tabular}{p{4cm}p{3cm}p{3cm}}
@@
 
-        This shows a significant benefit of the ``smart'' strategy, in the considered use-cases, between 30 to 60\% gain depending on the examples.
+ \medskip
+        This shows a significant benefit of the ``smart'' strategy, in the considered use-cases, between 30\% and 60\% gain depending on the examples.
 
@@
 The formal definitions and properties of the open pNets model were
-published in \cite{henrio:Forte2016}. In this new work we describe an implementation of
+given in \cite{henrio:Forte2016}. In the current work we describe an implementation of
 the model and its semantics construction, including its interaction
 with the Z3 SMT engine.
-The implementation has two parts: the first is a finitary algorithm
+The implementation has two parts: the first is an algorithm
 that builds all possible combinations of synchronisations through the
 pNet hierarchical structure. The result is a so-called
-\emph{open-automaton}, which transitions contains predicates relating
+\emph{open-automaton}, whose transitions contain predicates relating
 the actions of the pNet holes and controllers. Some of the open
-transitions obtained at this step,  may
+transitions obtained at this step  may
 contain predicates which do not represent any possible concrete
 instantiations. 
-In the second part of the tool we use the SMT solver Z3 for checking the
+In the second part of the tool we use the SMT solver Z3 to check the
 satisfiability of the predicate in each open transition. 
@@
 properties enforced by the architectures through an encoding into open
-pNets.  This encoding\mdash which we intend to formalise and prove
-correct in a separate paper\mdash also opens the way for an extension
+pNets.  This encoding %\mdash which we intend to formalise and prove
+% correct in a separate paper\mdash 
+also opens the way for an extension
 of BIP architectures with the transfer of data among variables of
@@
 Naturally, our next goals after the generation of the open automata
-will be to model-check logical properties, and to check equivalence of pNets. While
+will be to model-check logical properties, and to check equivalences of pNets. While
 model-checking open automata  seems easy to define, equivalence
@@
 different structure. For bisimulation, we foresee that SMT methods
-will be the basis for comparison of open transitions. 
+will be the basis for comparing open transitions. 
 %However, the usual approach of computing bisimulation by partition
@@
 for analysing our symbolic transitions will not make the approach too expensive
-in term of computing time. We tried a
-slighly bigger example, assembling 2 Failure controllers. In~\cite{Avocs-RR}, we show that Z3 can check the
+in terms of computing time. In~\cite{Avocs-RR}, we show that, for a slighly bigger example of assembling two failure controllers, Z3 can check the
 satisfiablility of a 90K open transitions in a couple of minutes.
@@
 fresh one.
-The variables in each synchronization vector are considered local:
+The variables in each synchronisation vector are considered local:
 for a given pNet expression, we must have fresh local variables for
@@
   The second rule ({\bf Tr2}) deals with pNet nodes: for each possible
-  synchronization vector applicable to the rule subject, the premisses
+  synchronisation vector applicable to the rule subject, the premisses
   include one {\em open transition} for each sub-pNet involved, one possible
@@
 %   leaves of the pNet, not only those involved in the chosen
-%  synchronization vector.
+%  synchronisation vector.
 
@@
 algorithm terminates. The following theorem shows that an open-pNet
-with finite synchronization sets, finitely many leaves and
+with finite synchronisation sets, finitely many leaves and
 holes, and each PLTS at leaves having a finite number of states and
@@
 Given an open pNet $pnet=\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $l_i^{i\in L}$ and holes $h_j^{j\in
-  J}$, if the sets $L$ and $J$ are finite, if the synchronization vectors of all pNets 
+  J}$, if the sets $L$ and $J$ are finite, if the synchronisation vectors of all pNets 
   included in  $pnet$ 
@@
 In addition, and for convenience, we provide one generic construct for
-parameterized actions named FUN, which can accept any number of
+parameterised actions named FUN, which can accept any number of
 arguments of any sort. The result type, though, can only be $Action$,
@@
 \begin{example}
-  For our BIP use-case, we have built (see Fig.\ref{schema:smt-lib}):
+  For our BIP use-case, we have built (see Figure\ref{schema:smt-lib}):
   \begin{lstlisting}
@@
 %%   checking. Every term of the predicate is declared as an
-%%   \texttt{assert} in Z3. A constant action or a parameterized
+%%   \texttt{assert} in Z3. A constant action or a parameterised
 %%   expression is easy to get from the internal list storing the objects
@@
 
-In Fig.~\ref{schema:ots} we display the same OTs in a more human friendly format (but manualy translated into latex).
+In Figure~\ref{schema:ots} we display the same OTs in a more human friendly format (but manualy translated into latex).
 
@@
 We build a larger system by composing several subsystems. In the
-example here (Fig.~\ref{schema:scaleup}), we use two Failure
+example here (Figure~\ref{schema:scaleup}), we use two Failure
 Monitoring modules. 
@@
 \QIN{
-We apply several structural rules to generate the predicates restricting the composition of the subnets by synchronization vectors.
+We apply several structural rules to generate the predicates restricting the composition of the subnets by synchronisation vectors.
 The predicates may contain some redundancy if there are variables in middle level are matching other variables both in lower and higher level at the same time. 
@@
     \item $I, J$ is the set of indices.
-    \item $k$ is the indices of the synchronization vectors.
-    \item $SV$ is the set of the synchronization vectors.
+    \item $k$ is the indices of the synchronisation vectors.
+    \item $SV$ is the set of the synchronisation vectors.
     \item $Vars()$ is the function that gets all the variables in the object.
-    \item $\alpha$ and $\alpha^{'}$ is the element of the  the synchronization vector.
+    \item $\alpha$ and $\alpha^{'}$ is the element of the  the synchronisation vector.
 \end{itemize}
@@
 %    \item (1) The predicates of the subnets: The result actions of the sub-OTs. Others are ground.
-%    \item (2) The chosen synchronization vector: If the result is also one of the elements, it is also the intermediate variable. Otherwise, all of the parameters are ground.
+%    \item (2) The chosen synchronisation vector: If the result is also one of the elements, it is also the intermediate variable. Otherwise, all of the parameters are ground.
 %    \item (3) Hole behaviours: Ground.

### 2019-03-17 2019-ActaInformatica/ActaInformatica.tex
very minor changes

@@
 works extended the basic behavioural models based on labelled
-transition systems to formalize value-passing or parameterised systems, using
+transition systems to formalise value-passing or parameterised systems, using
 various symbolic encodings of the
 transitions~\cite{deSimone85,Larsen87,HennessyLin:TCS95,Linconcur96}. 
-In \cite{Linconcur96}, Lin considered value-passing CCS, for which he
+In \cite{Linconcur96}, Lin considered value-passing CCS \cite{Milner89}, for which he
 developed a symbolic behavioural semantics, and developed algorithms for checking symbolic bisimulations.
@@
 method for these processes. 
-Later on, symbolic semantics were extended to the $\pi$-calculus and decision algorithms for various symbolic bisimulations were proposed \cite{Li99,Deng2001}. However, no
+Later on, symbolic semantics were extended to the $\pi$-calculus \cite{Milner99} and decision algorithms for various symbolic bisimulations were proposed \cite{Li99,Deng2001}. However, no
 practical verification platform has been developed to use this kind of approaches to provide proof methods for
@@
 
-Parameterised Networks of synchronised Automata (pNets) were proposed
+Parameterised Networks of Synchronised Automata (pNets) were proposed
 to give a behavioural specification formalism for distributed
@@
 verifying distributed systems, as the intermediate language for various
-high-level languages. The high-level languages in VerCors formalize
-each component of a distributed system and their composition.
+high-level languages. The high-level languages in VerCors formalise
+each component of a distributed system and their composition. The model of
 pNets provides the core low-level semantic formalism for VerCors, and
@@
 hierarchical level defines the possible synchronisation of the lower levels.
-Traditionally, pNets have been used to formalize fully
+Traditionally, pNets have been used to formalise fully
 defined systems or softwares. But we want also to define and reason
@@
 open automaton in which open transitions contain logical predicates
-expressing the relations between the behaviour of the holes, and the
-global behaviour of the system. In previous work,
+expressing the relations between the behaviour of the holes and the
+global behaviour of a system. In previous work,
 only a sketch of a procedure allowing for computing these semantics was
@@
 that we use here for satisfiability of open transitions will be
-similar with what we need when proving (symbolic) equivalence between open
+similar to what we need when proving (symbolic) equivalence between open
 transitions.
@@
 model, will also hold by construction on the generated code.
-BIP Architectures~\cite{AttieBBJS16-architectures-faoc} formalise
+BIP architectures~\cite{AttieBBJS16-architectures-faoc} formalise
 design patterns, which enforce global properties 
@@
 In Section \ref{section:implementation} we present an algorithm to compute this semantics, including the interaction with Z3.
-In Section~\ref{section:examples} we give a few use-cases, in particular, a BIP
+In Section~\ref{sec:cases} we give a few use-cases, in particular, a BIP
 architecture from the nano-satellite case-study. 
@@
 
-\section{Background: pNets definition}
+\section{Preliminaries}
 \label{section:pnets}
@@
 
-pNets are tree-like structures, where the leaves are either
+A pNet has a tree-like structure, where the leaves are either
 \emph{parameterised labelled transition systems (PLTSs)}, expressing the
@@
 %follows:
-The symbole $a_i^{i\in I}$
+The symbol $a_i^{i\in I}$
 denotes a family of elements $a_i$ indexed over the
@@
 When this is unambiguous, we shall use notations for sets, and typically write
-``indexed set over I'' which formally means multisets, and
+``indexed sets over I'' which formally means multisets, and
 write $x\in a_i^{i\in I}$ to mean $x=a_i$ for some $i\in I$.  An empty
@@
 the low-level behaviour of possibly very different
-programming languages, we do not want to impose one specific algebra
+programming languages, we do not impose one specific algebra
 for denoting actions, nor any specific communication mechanism. So we
@@
 %
-%Without loss of generality and to simplify the formalization, we suppose 
+%Without loss of generality and to simplify the formalisation, we suppose 
 %here that variables are local to 
@@
 %% the sub-pNets.
-The relation between actions of a pNet and those of its sub-pNets
+The relation between the actions of a pNet and those of its sub-pNets
 %% internal actions is
-are given by  \emph{synchronisation vectors}, which %% : a
+is given by  \emph{synchronisation vectors}, which %% : a
 %% synchronisation vector 
@@
 	here a simple example based on the ``Enable'' operator of the LOTOS language.
-	In Figure \ref{schema:enable-pnets}, we show 2 possible encodings of the  
+	In Figure \ref{schema:enable-pnets}, we show two possible encodings of the  
 	``Enable'' operator.
@@
 	In Figure \ref{schema:enable-composed}, we enrich our example by
-	composing 2 occurences of the Enable1 pNet. For simplicity,
+	composing two occurences of the Enable1 pNet. For simplicity,
 	we only represent one instance of the synchronisation vector set,
@@
 SMTlib declarations (\texttt{declare-datatypes} and
-\texttt{declare-fun}). We also formalize a condition of well-formedness of pNets to ensure that the generated code is correct,
+\texttt{declare-fun}). We also formalise a condition of well-formedness of pNets to ensure that the generated code is correct,
 and will not raise runtime errors in the SMT engine. Note that the

### 2019-03-17 2019-ActaInformatica/ActaInformatica.tex
more changes

@@
 
+\renewcommand{\pLTS}{PLTS}
+
 \newcommand{\orcid}[1]{\href{https://orcid.org/#1}{ORCID:~{#1}}}
@@
 
-\section{Operational Semantics for Open pNets}
+\section{Operational Semantics of Open pNets}
 \label{section:op-semantics}
@@
 open automaton are a restricted form of PLTSs, where labels are
-parametrised actions, but include no guard nor assignments.
+parametrised actions, but include neither guard nor assignments.
 
@@
         % a set  $\langle S_i,s_{0 i}, \rightarrow_i\rangle^{i\in I}$ of LTSs,
-        a set $J$ of holes, %with sorts $Sort_j^{j\in J}$
+        a set $J$ of holes %with sorts $Sort_j^{j\in J}$
         and a set of states $\mathcal{S}$ is a structure of the form:	
@@
         substitution $\{x_k\gets e_k\}^{k\in K}$  
-	where $x_k$ are variables of $s'$ and $s'_i$, whereas $e_k$ are
-        expressions over the other variables of the open transition.
+	where $x_k$ is a variable of $s'$ or $s'_i$, whereas $e_k$ is an
+        expression over other variables of the open transition.
 \end{definition}
@@
 		$t\in \mathcal{T}$, there exist $I'$, $J'$ with $I'\subseteq I$, $J'
-		\subseteq J$, such that $t$ is an open transition over $J'$,
+		\subseteq J$, such that $t$ is an open transition over $J'$
 		and  $\mathcal{S}$.
@@
   in structured states as $\triangleleft\ldots\triangleright$).
-  For any pNet p, let $\overline{\mathit{Leaves}} = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be the set of PLTS at its leaves,
+  For any pNet p, let $\overline{\mathit{Leaves}} = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be the set of PLTSs at its leaves,
   then $\mathit{States}(p) = \{\ostate{s_i^{i\in L}}
   |\, \forall i\in L. s_i \in S_i\}$.
-A PLTS being its own single leave:
+A PLTS could be its own single leave:
   $\mathit{States}(\mylangle S,s_0, \to\myrangle) = \{\ostate{s}|\, s \in S\}$.
@@
   Transition $OT_1$ of the pNet $EnableCompl$ is generated by
-  combination of the first vector of its root node, with
-  the second vector of its $2^{nd}$ node. Its generated predicate is
-  trivialy true. The global states shows that controler $C_3$ has
+  combining the first vector of its root node with
+  the second vector of its second node. Its generated predicate is
+  trivially true. The global state shows that controler $C_3$ has
     changed from state 0 to 1.
@@
 % $\forall i \in L.\, finite{(states(l_i))} \text{ and } l_i$ 
-$l_i $ has a finite number of state variables for each $i\in I$, then the semantics of $pnet$ is an open automaton 
+$l_i $ has a finite number of state variables for each $i\in I$. Then the semantics of $pnet$ is an open automaton 
 %$\mathcal{T}$ 
@@
 the semantic rules following the structure of the pNet.
-When applied to a PLTSs at the leaves, we simply take the PLTS transitions of the
+When applying a rule to a PLTS at the leaves, we simply take the PLTS transitions of the
 corresponding local state and use the semantic rule to build the OT\footnote{%
@@
 }.
-When applied to a pNet node we use two methods, combining and
+When applying a rule to a pNet node we use two methods, combining and
 matching, to generate the open transitions in a hierarchical manner,
-as shown in Alg.~\ref{alg2}. This method directly manages the
+as shown in Algorithm~\ref{alg2}. This method directly manages the
 holes of the node, so \emph{MakeTransitions} is never called on a hole.
@@
 %% \st{$L = {s_1, s_2, ...,  s_n}$;}
-We denote $\overline{ot}_i$ the set of open
+We denote by $\overline{ot}_i$ the set of open
 transitions of the $i$-th
@@
 ``$-$'' means that the subnet is not involved.
-The combination $\overline{comb}$, a set of n-tuples, is the
+The combination $\overline{comb}$, a set of $n$-tuples, is the
 cartesian product:  
@@
 Here, we only detail the construction of the predicate.
-Suppose $sv = \left((a'_i)^{i\in I} (b'_j)^{j\in J}\rightarrow v'\right) \in SV$ is a synchronisation vector, $G_k$ is its guard, 
+Suppose that $sv = \left((a'_i)^{i\in I} (b'_j)^{j\in J}\rightarrow v'\right) \in SV$ is a synchronisation vector, $G_k$ is its guard, and
 $C = ({ot}_i)^{i \in [1,n]} \in \overline{comb}$ is a tuple of open transitions such that, for each $i \in [1,n]$, either $ot_i = -$, or the result action of $ot_i$ is $a_i$.
@@
 The ``Modulo Theory'' part of SMT solvers is important here, as
-the solver can use specific properties of each action algebra.
+the solvers can use specific properties of each action algebra.
 
@@
 
-Algorithm~\ref{alg3} implement this new stategy: \TODO{Explain
+Algorithm~\ref{alg3} implements this new stategy: \TODO{Explain
   significant detials}
@@
 Our implementation submits satisfiability requests to
-Z3 using its JAVA API. Here, for readability, we
+Z3 using its Java API. Here, for readability, we
 show the Z3 code using its SMT-LIB input language.
@@
 particular because of structured names for the fresh variables generated
-by the algorithm, allowing tracability of the result~\cite{Avocs-RR}.
-
-Figure~\ref{schema:smt-lib} shows the translation of the
-transition of Figure~\ref{schema:unsat-ot}
+by the algorithm, allowing for tracability of the result~\cite{Avocs-RR}.
+
+Figure~\ref{schema:smt-lib} shows the translation of  Figure~\ref{schema:unsat-ot}
 in the SMTlib syntax.
@@
 engine. It should be clear that more involved examples will require
-reasonning about predicates of various data types. Z3 provides theories for reasonning
+reasoning about predicates of various data types. Z3 provides theories for reasonning
 about integers, bitstrings, enumerated types, arrays, etc.
@@
 recursive structures, the user will have to develop its own theories.
-Decidability of these theories will condition the completeness of the
+Decidability of these theories will condition on the completeness of the
 satisfiability check, and the decidability of model-checking or
@@
 names from our example.
-Additionally, we will include axiomatization of any required functions
+Additionally, we will include axiomatisation of any required functions
 and predicates of the presentation data-types.
@@
 reset, unless a resumption is registered within $\mathrm{Max}$ time
-units (more details in Sect.~\ref{section:resultOA}).
+units (more details in Section~\ref{section:resultOA}).
 
@@
 coordinator component is encoded as a PLTS, the operand
-component\mdash as a hole; connectors of the BIP model are encoded as
+component as a hole; connectors of the BIP model are encoded as
 synchronisation vectors.  Each connector that does not involve
@@
 algorithm. For reasons of readability, we do not show the full
-details of the open transitions on this figure. Below we list the
+details of the open transitions in this figure. Below we list the
 first three of them (full details available in \ref{TimerRR}). 
@@
 pNet hierarchical structure. The result is a so-called
-\emph{open-automaton}, whose transitions contain predicates relating
+\emph{open automaton}, whose transitions contain predicates relating
 the actions of the pNet holes and controllers. Some of the open
@@
 In~\cite{henrio:Forte2016}, we
-have already found the FH-bisimulation, %inspired
+have already found the FH-bisimulation %inspired
 %by~\cite{deSimone85},

### 2019-03-18 2017-Xudong-SMT/ActaInformatica.tex
Inserted FailureTimerv2-2 and its results.

@@
   \centering
-  \includegraphics[width=\columnwidth]{ActaXFIG/BIPspec-ArchFailureTimer-v2-1a}
+  \includegraphics[width=\columnwidth]{ActaXFIG/BIPspec-ArchFailureTimer-v2-2}
   \caption{The BIP specification of the Failure Monitor architecture}
@@
   \centering
-  \includegraphics[width=0.9\columnwidth]{ActaXFIG/FailureTimerPNET-v2-1a}
+  \includegraphics[width=0.9\columnwidth]{ActaXFIG/FailureTimerPNET-v2-2}
   \caption{pNet encoding of the Failure Monitor architecture}
@@
 
-For this example, the tool (using Algorithm 1) builds 218 open transitions, whereof 206
+For this example, the tool (using Algorithm 1) builds 258 open transitions, whereof 248
 are detected unsatisfiable by Z3.  The resulting open automaton, with
-4 reachable global states (out of the possible 6) and 12 open
+3 reachable global states (out of the possible 6) and 10 open
 transitions, is shown in Fig.~\ref{schema:resultOA1}.
@@
 \begin{figure}[t]
-  \centerline{\includegraphics[width=12cm]{ActaXFIG/FailureTimerOA-v2-1a}}
+  \centerline{\includegraphics[width=12cm]{ActaXFIG/FailureTimerOA-v2-2}}
   \caption{Open Automaton for the Failure Monitor architecture}
@@
 
-Failure Monitor enforces 1)~the safety property \emph{``the
+Failure Monitor enforces \noteEM{NO!!!}1)~the safety property \emph{``the
   system reset never happens, unless asked for by a timeout
@@
 
-\subsection{Composing 2 FailureTimer BIP Architecture}
+\subsection{Composing 2 FailureTimer BIP Architectures}
 \noteInEM{Modifications stopped here}
@@
   \centering
-  \includegraphics[width=0.9\columnwidth]{XFIG/FailureTimerPNET-v4}
-  \caption{The open pNet encoding the Failure Monitor architecture (\ref{fig:schema:ArchFailure:BIP}) without the Max Progress priority model}
+  \includegraphics[width=0.9\columnwidth]{ActaXFIG/FailureTimerPNET-v2-2}
+  \caption{The open pNet encoding the Failure Monitor architecture (\ref{fig:schema:ArchFailure:BIP})}
   \label{fig:FailureTimer:pNet}

### 2019-03-18 2017-Xudong-SMT/ActaInformatica.tex
v2-2, new version

@@
 
+In the conception of the Nano satellite Software \cite[], the Failure
+Timer architecture was used to control several processes
+communicating on the common bus. Timeout signals (``$ask$''), resets,
+and the passing of time ($tick$) were synchronised in the global
+system.
+
+In Figure~\ref{schema:ArchFailure:BIP:Double} we show the combination
+of two FailureTimer architectures, with their respective controlled
+processes.
+
 \begin{figure}[t]
   \centering
-  \includegraphics[width=0.9\columnwidth]{ActaXFIG/FailureTimerPNET-v2-2}
-  \caption{The open pNet encoding the Failure Monitor architecture (\ref{fig:schema:ArchFailure:BIP})}
-  \label{fig:FailureTimer:pNet}
+  \includegraphics[width=\columnwidth]{ActaXFIG/BIPspec-DoubleArchFailureTimer-v2-2}
+  \caption{The BIP specification of the Failure Monitor architecture}
+  \label{schema:ArchFailure:BIP:Double}
 \end{figure}
 
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=0.9\columnwidth]{XFIG/TimerOADetailed}
-  \caption{The open Automaton of the Failure Monitor Architecture}
-  \label{fig:ArchFailure:OA}
-\end{figure}
-
-Figure \ref{fig:ArchFailure:OA} shows the open automaton built by our
-algorithm. For reasons of readability, we did not show the full
-details of the open transitions on this figure. Below we list the
-first 3 of them (full details available in \ref{TimerRR}). 
-This automaton has 12 transitions, including those encoding various
-possible firing of some interactions (e.g. OT 2 and 3 for
-{\PortFail}). It looks like the rough behaviour is
-reasonable, although a detailed study shows that the property stated
-above does not hold, because of the
-{\PortFail} loops on states $11$ and $12$. This is because we did not
-use the maximal progress assumption here. If we do, we get the
-corrected behaviour in Figure \ref{fig:ArchFailure:OA-MaxProgress}, in
-which $OT_7$ has disappeared, and $OT_2$ and 
-$OT_{10}$ have been restricted to $b0=\false$.
-
-\bigskip
-\noindent
-$  OT_1  = \openrule
-{\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
-{\ostate{00} \OTarrow{init} \ostate{11}}
-$
-
-\medskip    
-\noindent
-$  OT_2  = \openrule
-{\{B\mapsto fail(b0)\},\\
-  t<GetMax(z) \land b1=false \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),\\
-  \{z:=z1\} }
-{\ostate{11} \OTarrow{fail} \ostate{11}}
-$
-\medskip
-
-\noindent
-  $  OT_3  = \openrule
-  {\{B\mapsto fail(b0)\},\\
-    t<GetMax(z) \land b1=true \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),\\
-    \{z:=z1\} }
-  {\ostate{11} \OTarrow{fail} \ostate{12}}
-  $
-  \medskip
-
-  \begin{figure}[t]
-  \centering
-  \includegraphics[width=\columnwidth]{XFIG/TimerOAMaxProgress}
-  \caption{The open Automaton of the Failure Monitor Architecture,
-    with Maximal Progress}
-  \label{fig:ArchFailure:OA-MaxProgress}
-  \end{figure}
-
-  \TODO{Eric: Explain}
-\begin{itemize}
-\item $OT_2$ and $OT_{10}$ have changed because $b0=true$ is no longer possible
-\item $OT_7$ has disappeared because it is now unsat.
-\end{itemize}
+%% \begin{figure}[t]
+%%   \centering
+%%   \includegraphics[width=0.9\columnwidth]{ActaXFIG/DoubleFailureTimerPNET-v2-2}
+%%   \caption{The open pNet encoding the Failure Monitor architecture (\ref{fig:schema:ArchFailure:BIP})}
+%%   \label{fig:FailureTimer:pNet}
+%% \end{figure}
+
+%% \begin{figure}[t]
+%%   \centering
+%%   \includegraphics[width=0.9\columnwidth]{XFIG/DoubleTimerOA-v2-2}
+%%   \caption{The open Automaton of the Failure Monitor Architecture}
+%%   \label{fig:ArchFailure:OA}
+%% \end{figure}
 
@@
 		FailureTimer    			&
-                12/235 OTs           &
-                12/180 OTs
+                12/364 OTs           &
+                12/167 OTs
                 \\\specialrule{0em}{1pt}{1pt}
 
-                (no Max Progress)&
-                1253 UNSAT           &
-                812 UNSAT
-                \\\specialrule{0em}{1pt}{1pt}
   		&
-                1253 ms 				&
-                812 ms  
+                1080 ms 				&
+                563 ms  
 		\\\hline\specialrule{0em}{1pt}{1pt}
 		FailureTimer X 2    			&
-                37/3136 OTs           &
-                37/2416 OTs
+                25/8964 OTs           &
+                25/1255 OTs
                 \\\specialrule{0em}{1pt}{1pt}
@@
 		&
-                8923 ms 				&
-                6798 ms
+                18088 ms 				&
+                3266 ms
 
@@
 
-        This shows a significant benefit of the ``smart'' strategy, in the considered use-cases, between 30 to 60\% gain depending on the examples.
+        This shows a significant benefit of the ``smart'' strategy, in the considered use-cases, between 30 to 80\% gain depending on the examples.
 

### 2019-03-19 2017-Xudong-SMT/ActaInformatica.tex
OT examples, and Xudong TODOs

@@
 
-\begin{example}[An open transition]\TODO{change for Enable example}
+\begin{example}[Open transitions]
   Transition $OT_1$ of the pNet $EnableCompl$ is generated by
@@
     changed from state 0 to 1.
-
-    \TODO{add another example to illustrate assignements/Post}
 
@@
 	\end{mathpar}
+
+If we use the data-oriented pNet Enable2 from Figure \ref{schema:enable-pnets} to building a similar
+``P>>(Q>>R)'' expression, the corresponding open transition would be:
+
+  \label{OT:example-1}
+        \begin{mathpar}
+	  OT_2  =
+          \inferrule*[myfraction=\reddottedrule]
+	{\{\xrightarrow{\delta(x3)}_P ~~
+          \xrightarrow{acc(x3)}_Q \} ~~
+          [v_1=0 \land v_2 = 0 \land \forall z. acc(x3) \neq
+            \delta(z)] ~~ \{v1:=1\}
+        }
+	{\ostate{0,0} \xrightarrow {\underline{\delta(x3)}} \ostate{0,0}}
+	\end{mathpar}
+        where $v_1$ and $v_2$ are respectively the state variables of
+        the first and second Enable2 pNet. Indeed the global
+        state space of this version is reduced to $\ostate{0,0}$, and
+        the state change is replaced by the assignment ``$v_1:=1$''.
+
 \end{example}
@@
 \EndWhile
-\State \ERIC{Prune the unsatisfiable open transitions in $L$ using the SMT
-solver; only keep reachable global states;}
+\State \TODO{Xudong:Prune the unsatisfiable open transitions in $L$ using the SMT
+  solver;
+   and add a call to ``compute the reachable sub-automaton'';}
 \State \Return $\mathit{OA}=(\mathit{InitState}(P),L)$;
@@
 incorrect, but is naturaly not an optimal representation. So we prune
-these UNSAT transitions: at the root of the pNet, the predicate of each OT is translated
-into SMTlib assertions, and checked for satisfiability.
-The final open automaton includes all satisfiable OTs, and the set of
-reachable global states.}
+these UNSAT transitions: at the end of the open automaton generation,
+the predicate of each OT is translated 
+into SMTlib assertions, and checked for satisfiability.\\
+Then we compute the set of reachable transitions and states to build
+the final open automaton.}
 %By construction, due to the
@@
   \item if some subnet is marked as inactive in the vector, and the
-    chosen combination has an active behaviour at this position,
+    chosen combination has an active behaviour at this position, or vice-versa;
   \item if some subnet action expression in the vector does not match (by
-    pattern-matching) the corresponding action expression in $C$,
+    pattern-matching) the corresponding action expression in $C$;
   \item or if the whole set of active subnet actions in the vector
     cannot be matched (by unification) with the corresponding action expressions
-      on the tuple $C$.
+      on the tuple $C$ (this is strictly stronger than the
+      previous filter). 
 \end {itemize}
@@
 In a pLTS, there may be several incoming transitions 
-that assign potentially different values to a state variable.
+that assign potentially different (symbolic) values to a state variable.
 To handle such cases, the algorithm manages, for each pLTS state, a
@@
 For a global state in the open automaton, the set of state
-variables (which may be used in a transition) %% will simply be
+variables (which may be used in an outgoing transition) %% will simply be
 is the disjoint union
@@
 global state.
+\TODO{Xudong: speciy more precisely what is done, and at which point
+  in the MakeTransitions algo}
 %There are some assignment on the variables in each of states of the pLTS (state variables), or just as global states of it (global variables).
@@
 In order to avoid such mistakes,
-\TODO{these assignment sets collect potential assignments from all OTs
-  in the generated automaton. If we minimize the generated state
+\TODO{Eric: these sets of assignment collect potential assignments from all OTs
+  in the generated automaton. If we prune the generated state
   space, we will get less assignements, and potentialy also get better
-  minimization... }
+  minimization... May be move this to ``smart'' section}
 
@@
 approximation, and potentialy more informations, that can be used to
-the SAT check of subsequent transitions.}
-\TODO{Beware, I think this is dangerous... Xudong, do we really use
-  assignment information in SAT checking ? In the ``smart'' version, I
-  think we must NOT use it, because we do not yet have collected all
-  possible assignments.}
+the SAT check of subsequent transitions. But we \emph{cannot} use this
+assignment information in the ``on-the-fly'' SAT checking, because
+they cannot be complete before exploring (at least) all the reachable
+state space. So the smart algorithm performs in to steps: during the
+first step, the SAT check is done without using any assignment set
+information. Then after completion of this step, we perform another
+SAT check of all transitions from step1, but this time using the
+assignment information. This may reduce the reachable state space. If
+we want to be sure the obtained automaton is minimal, we should
+iterate this step until a fix-point is reached. But in practical cases, very
+little will be gained, and leaving some UNSAT transitions in the
+symbolic automaton is still logicaly correct.}
 
@@
 
-\TODO{Candidate theorems:
-  - All reachable states from algorithm 1 are kept by Algorithm 3\\
-  - Algorithm 3 computes an open automaton that is minimal with
-  respect of SAT checking decidability.\\
-  I have problem with minimality... Because of the ``two phases'' SAT
-  checking that we have now, because we cannot use incomplete sets of
-  variable assignments during the ``smart'' phase, and use them later,
-minimality becoomes trivialy equivalent in the original and smart algorithms...}
+\TODO{Candidate theorems: Xudong: state the theorems, and sketch the proofs}
+
+\ERIC{First the good case: if we have no assignments to state variables in
+the system, then we can directly compute the reachable part of the
+automaton using the on-the-fly algorithm.}
+
+\begin{theorem}[Correctness without assignments]
+  \label{Th:finiteness}
+If a pNet contains no assignment to state variables, then the smart
+algorithm, without final reachability computation, computes exactly
+the same open automaton as algorithm 1.
+  \end{theorem}
+
+\TODO{Xudong: proof}
+
+\ERIC{But in presence of assignments, we need to collect all of them
+  before using the assignment information to refine the SAT
+  checking. Still the smart strategy will explore a reduced state
+  space, but not the minimal one (discussion later)}
+
+\begin{theorem}[Correctness without assignments]
+  \label{Th:finiteness}
+In the general case, then the smart
+algorithm, with a final reachability computation, computes exactly
+the same open automaton as algorithm 1.
+\end{theorem}
+
+\TODO{Xudong: proof}
+
+\TODO{Eric : provide counter-example for smart with unsing incomplete
+  assignment sets}
 
@@
 		FailureTimer    			&
-                12/364 OTs           &
-                12/167 OTs
+                12/396 OTs           &
+                12/192 OTs
                 \\\specialrule{0em}{1pt}{1pt}
@@
   		&
-                1080 ms 				&
-                563 ms  
+                1220 ms 				&
+                687 ms  
 		\\\hline\specialrule{0em}{1pt}{1pt}

### 2019-03-20 2017-Xudong-SMT/ActaInformatica.tex
Improve Alg 1, add more explanation for Alg 1,2
In Alg 1, add two functions at the end of the algorithm, the explanation part is just below the Alg 1.
Add more explanation in 4.1, as Alg 2 is just for pNets, there is no more things to add.

@@
 \EndWhile
+\State \QIN{\texttt{filterUnsatTransition}(L)}
+\State \QIN{\texttt{filterNoPrecursor}(L)}
 \State \TODO{Xudong:Prune the unsatisfiable open transitions in $L$ using the SMT
@@
 %through a sequence of satisfiable open transitions.
+
+\QIN{The function \texttt{filterUnsatTransition}() realizes exactly what described above, completing the open transitions pruning work.}
+
+\QIN{The function \texttt{filterNoPrecursor}() detects the unreachable states which has no precursor states in the pruned automaton and removes them.}
 
@@
 that assign potentially different (symbolic) values to a state variable.
-To handle such cases, the algorithm manages, for each pLTS state, a
-list of expressions collected from the assignments of each state
-variable. %% $v$.
+To handle such cases, the algorithm manages a
+list of assignment expressions for each pLTS state. 
+\QIN{Every time the MakeTransitions
+algorithm is applied on a pLTS, it collects the expressions from the $Post$ in each transition.
+As there is no assignments collecting work on a pNet node, it is not shown in Algorithm~\ref{alg2}.}
+%% $v$.
 %% The list we used contains triples <$v$, $S$, $AssignRH$> 
@@
 % ``global variables'', defined in all states of the pLTS.
+
 For a global state in the open automaton, the set of state

### 2019-03-20 2017-Xudong-SMT/ActaInformatica.tex
lot of text in section "smart"

--- 2019-03-19 2017-Xudong-SMT/ActaInformatica.tex
@@
 
-In Fig.~\ref{schema:EnableEncodings}, we show examples of these
-constructs, with two pLTSs, one hole and one pNet node encoding our running example.
+In Figures~\ref{schema:enable-pnets},\ref{schema:enable-composed}, we show
+examples of these constructs, with two pLTSs, one hole and one pNet
+node encoding our running example.
 
@@
 \label{section:example}
-\TODO{Taken from \cite[Forte]}
 
@@
         In this example we use \emph{synchronised
-          actions}, to express actions that cannot be further synchronised, like the
+          actions}, to express actions that cannot be further synchronised, likesimilar to the
         $\tau$ silent action of CCS. We denote them as any action expression with the text
@@
 \EndWhile
-\State \TODO{Xudong:Prune the unsatisfiable open transitions in $L$ using the SMT
-  solver;
-   and add a call to ``compute the reachable sub-automaton'';}
-\State \Return $\mathit{OA}=(\mathit{InitState}(P),L)$;
+\State \QIN{$\mathit{L1}$ = \texttt{filterUnsatTransitions}($\mathit{L,Assignements}$)}
+\State \QIN{$\mathit{OA}$ = \texttt{makeReachableSubAutomaton}($\mathit{InitState}(P)$,$\mathit{L1}$)}
+\State \Return $\mathit{OA}$;
 
@@
 the predicate of each OT is translated 
-into SMTlib assertions, and checked for satisfiability.\\
+into SMTlib assertions, and checked for satisfiability (function \texttt{filterUnsatTransitions}).\\
 Then we compute the set of reachable transitions and states to build
 the final open automaton.}
-%By construction, due to the
-%satisfiability test in line 6, it only produces the set of states reachable
-%through a sequence of satisfiable open transitions.
 
@@
 that assign potentially different (symbolic) values to a state variable.
-To handle such cases, the algorithm manages, for each pLTS state, a
-list of expressions collected from the assignments of each state
-variable. %% $v$.
-%% The list we used contains triples <$v$, $S$, $AssignRH$> 
-%% where $v$ is the variable in pLTS, $S$ is its owner state and
-%% $AssignRH$ is a list of expressions over other variables in the right
-%% hand side of assignments of $v$.
-% As a pragmatic extension to the formal definition, we also manage
-% ``global variables'', defined in all states of the pLTS.
+To handle such cases, the algorithm manages a
+list of assignment expressions for each pLTS state. 
+\QIN{The only assignments happen on state variables, at pLTS level: every time the MakeTransitions
+algorithm is applied on a pLTS, it collects the expressions from the $Post$ in each transition.
+% As there is no assignments collecting work on a pNet node, it is not
+% shown in Algorithm~\ref{alg2}.
+}
+
 For a global state in the open automaton, the set of state
-variables (which may be used in an outgoing transition) %% will simply be
+variables (which may be used in an outgoing transition) 
 is the disjoint union
 of sets of state variables of the individual pLTS states constituting this
-global state.
-\TODO{Xudong: speciy more precisely what is done, and at which point
-  in the MakeTransitions algo}
-%There are some assignment on the variables in each of states of the pLTS (state variables), or just as global states of it (global variables).
-There is usually not only one assignment for a state variable, miss of them may drop the unsatisfiable results.
-In order to avoid such mistakes,
-\TODO{Eric: these sets of assignment collect potential assignments from all OTs
-  in the generated automaton. If we prune the generated state
-  space, we will get less assignements, and potentialy also get better
-  minimization... May be move this to ``smart'' section}
+global state. \ERIC{The final assignment sets are assembled when building the
+open automaton from the reachable transitions.}
 
@@
 \subsection{Computing reachable state space on the fly}
-\TODO{add a high level description of the new strategy, discuss
-  decidability/approximation of the SAT checking, express some
-  ``minimality'' property}
-
-The basic algorithm from the previous section potentialy explores some
+
+\ERIC{The basic algorithm from the previous section potentialy explores some
 areas of the global state-space that will not be reachable after
@@
 create, and submit to Z3, the OTs at the ``border'' of the state-space, but
-not the transitions issued from non-reachable global states.
-
-\ERIC{But there is more to this. As mentionned above, we collect all
+not the transitions issued from non-reachable global states. We use
+this idea to create our ``smart'' algorithm.}
+
+But there is more to this. Due to the symbolic nature of the
+  transitions, reachability is not as easy to define as in standard
+  models. As mentionned above, we collect all
 possible (symbolic) assignments of state variables, in the
 computed open automaton. By avoiding building the OTs coming from
-unreachable states, we also avoid adding the corresponding assignments
+some unreachable states, we also avoid adding the corresponding assignments
 to the variables of their target states. The set of possible
-assignments is an over approximation of possible values of the
+assignments computed by the algorithm is an over approximation of
+possible values of the 
 variables of such state, so narrowing it means we get a better
-approximation, and potentialy more informations, that can be used to
-the SAT check of subsequent transitions. But we \emph{cannot} use this
+approximation, and potentialy more information, that can be used to
+the SAT checking of subsequent transitions. But we \emph{cannot} use this
 assignment information in the ``on-the-fly'' SAT checking, because
 they cannot be complete before exploring (at least) all the reachable
-state space. So the smart algorithm performs in to steps: during the
-first step, the SAT check is done without using any assignment set
+state space. So the smart algorithm performs in two steps: during the
+first step, the SAT checking is done without using any assignment set
 information. Then after completion of this step, we perform another
-SAT check of all transitions from step1, but this time using the
+SAT checking of all transitions from step1, but this time using the
 assignment information. This may reduce the reachable state space. If
@@
 iterate this step until a fix-point is reached. But in practical cases, very
-little will be gained, and leaving some UNSAT transitions in the
-symbolic automaton is still logicaly correct.}
-
-Algorithm~\ref{alg3} implement this new stategy: \TODO{Explain
-  significant detials}
+little will be gained, so the default implementation does only one
+step. Leaving some UNSAT transitions in the
+symbolic automaton is still logicaly correct.
+
+\TODO{Yuxin: I can add an example showing in detail why we cannot use
+  the assignment information on the fly. Do you think this is useful,
+  or id the explanation above sufficient ?}
 
@@
 %%\State Prune the unsatisfiable open transitions in $L$ using the SMT solver;
-\State \Return $\mathit{OA}=(\mathit{InitState}(P),L)$;
-
+\IfThenElse {(NonEmptyAssignmentSet($\mathit{L}$))}
+        {\State $\mathit{L1}$=filterUnsatTransitions($\mathit{L,Assignments}$);
+          \State \Return $\mathit{OA}$=makeAutomaton($\mathit{InitState}(P),L)$;}
+        {\State \Return $\mathit{OA}$=makeReachableSubAutomaton($\mathit{InitState}(P),L1)$};
 \end{algorithmic}  
 \end{algorithm}
+
+Algorithm~\ref{alg3} implement this new stategy: in line 5, it runs
+the satisfiability check on each OT generated from this global
+state. This check is done without using the assignment information, as
+discussed above. Only the OTs found SAT from this check will be added
+to $L$, and the corresponding target global state added to $U$ if
+necessary. This ensures that all explored global states are
+effectively reachable by a chain of SAT OTs.
+
+Then at the end of the residual loop, we do another traversal of the
+automaton, this time using the assignment information collected that
+far, and compute the final reachable sub-automaton. This step,
+naturaly, is only useful if there are some assignments.
 
@@
   before using the assignment information to refine the SAT
-  checking. Still the smart strategy will explore a reduced state
+  checking. Still, the smart strategy will explore a reduced state
   space, but not the minimal one (discussion later)}
@@
 
-\TODO{Eric : provide counter-example for smart with unsing incomplete
+\TODO{Eric : Eventually provide counter-example for smart with unsing incomplete
   assignment sets}

### 2019-03-20 2017-Xudong-SMT/ActaInformatica.tex
added Double result automaton

@@
 processes.
+In Figure~\ref{schema:ArchFailure:Double:OA} we show the resulting
+open automaton. Remark that it shows that th etwo timers are forced to
+be synchronous: each can only tick after the other has also started,
+and then they will tick, and timeout, synchrounously.
 
@@
   \includegraphics[width=\columnwidth]{ActaXFIG/BIPspec-DoubleArchFailureTimer-v2-2}
-  \caption{The BIP specification of the Failure Monitor architecture}
+  \caption{The BIP specification of two composed Failure Monitor architectures}
   \label{schema:ArchFailure:BIP:Double}
+\end{figure}
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=\columnwidth]{ActaXFIG/Double-OA}
+  \caption{The resulting automaton}
+  \label{schema:ArchFailure:Double:OA}
 \end{figure}

### 2019-03-21 2017-Xudong-SMT/ActaInformatica.tex
Correct the format of IfThenElse.
Modify the \algnewcommand{\IfThenElse}.
Use \quad as the indent for the ITE statements.
Polish Enable example, replace figures accordingly

@@
 \algnewcommand{\IfThen}[2]{\State \algorithmicif\ #1\ \algorithmicthen\ #2}% \IfThenElse{<if>}{<then>}
-\algnewcommand{\IfThenElse}[3]{\State \algorithmicif\ #1\ \algorithmicthen\ #2\ \algorithmicelse\ #3}% \IfThenElse{<if>}{<then>}{<else>}
+\algnewcommand{\IfThenElse}[3]{\State \algorithmicif\ #1\ \algorithmicthen\ #2\ \State \algorithmicelse\ #3}% \IfThenElse{<if>}{<then>}{<else>}
 %\DeclareMathOperator{\card}{card}
@@
 \ref{section:pnets} we give a description and a formal definition of
-the pNet model, as found in previous publications. Then in section
-\ref{section:examples} we present our use-case, based on a BIP
-architecture from the nano-satellite case-study. 
+the pNet model, as found in previous publications, and present a
+running example based on Lotos ``Enable'' operator.
 Section \ref{section:op-semantics} recalls briefly the operational semantics
@@
 used to compute this semantics, including the interaction with Z3, and
-shows the full result of the semantic computation on the running example.
+shows the full result of the semantic computation on the running
+example.
+In section \ref{section:use-cases} we show the result of the study of
+our running example, then explain a bigger use-case based on a BIP
+architecture from the nano-satellite case-study. We show the benefits
+drawn from the smart algorithm.
 Finally we conclude and discuss perspectives in Section
@@
 
-  \includegraphics[width=\linewidth]{XFIG/Enable1}
+  \includegraphics[width=\linewidth]{ActaXFIG/Enable1}
   \\[1.3ex]
- \includegraphics[width=\linewidth]{XFIG/Enable2}
+ \includegraphics[width=\linewidth]{ActaXFIG/Enable2}
   \caption{Two pNet encodings for  Enable }  \label{schema:enable-pnets}
@@
 \begin{minipage}{6cm}
-  \includegraphics[width=\linewidth]{XFIG/P-QR}
+  \includegraphics[width=\linewidth]{ActaXFIG/P-QR}
   \caption{Composed pNet for ``P>>(Q>>R)''}  \label{schema:enable-composed}
@@
 	``Enable'' operator.
-	In the Enable expression ``P>>Q'', an \texttt{exit(x)} statement within P
+	In the Enable expression ``P>>Q'', an \texttt{exit} statement within P
 	terminates the current process, carrying a value $x$ that
-	is captured by the \texttt{accept(x)} statement of Q.
+	is captured by the \texttt{accept} statement of Q.
 
@@
 	possible data type of the variable $x$, corresponding to the
-	statements \texttt{exit(x)} and \texttt{accept(x)}. Both $\delta(x)$
+	statements \texttt{exit} and \texttt{accept}. Both $\delta(x)$
 	and $acc(x)$ actions are
@@
 	from equality of actions. 
-	In the first encoding $Enable1$, in the upper part of
-	Fig. \ref{schema:enable-pnets}, we use a controller $C_1$ with two
+	In the first encoding $EnableState$, in the upper part of
+	Fig. \ref{schema:enable-pnets}, we use a controller $CState$ with two
 	states, and simple control actions $l, r, \delta$. The second encoding
-	$Enable2$ uses a data-oriented style, with a single state controller, and a
-	state-variable $s_0$, with values in $\{0,1\}$.
+	$EnableData$ uses a data-oriented style, with a single state controller $CData$, and a
+	state-variable $v$, with values in $\{0,1\}$.
 
@@
 	In Fig. \ref{schema:enable-composed}, we enrich our example by
-	composing 2 occurences of the Enable1 pNet. To simplify,
-	we only have represented one instance of the synchronisation vector set,
-	and of the controller.
+	composing 2 occurences of the EnableState pNet. In section
+        \ref{section:use-case:Enable} we show how these encodings can
+        be use to prove properties of the Enable operator.
 
@@
 \begin{example}[Open transitions]
-  Transition $OT_1$ of the pNet $EnableCompl$ is generated by
+  Transition $OT_1$ of the pNet $EnableStateCompLeft$ is generated by
   combination of the first vector of its root node, with
   the second vector of its $2^{nd}$ node. Its generated predicate is
-  trivialy true. The global states shows that controler $C_3$ has
+  trivialy true. The global states shows that controler $CState1$ has
     changed from state 0 to 1.
@@
           \inferrule*[myfraction=\reddottedrule]
-	{\{\xrightarrow{\delta(x3)}_P ~~
-          \xrightarrow{acc(x3)}_Q \} ~~
-          [\forall z. acc(x3) \neq \delta(z)]
+	{\{\xrightarrow{\delta(x2)}_P ~~
+          \xrightarrow{acc(x2)}_Q \} ~~
+          [\forall z. acc(x2) \neq \delta(y1)]
         }
-	{\ostate{0,0} \xrightarrow {\underline{\delta(x3)}} \ostate{1,0}}
+	{\ostate{0,0} \xrightarrow {\underline{\delta(x2)}} \ostate{1,0}}
 	\end{mathpar}
 
-If we use the data-oriented pNet Enable2 from Figure \ref{schema:enable-pnets} to building a similar
+If we use the data-oriented pNet $EnableData$ from Figure
+\ref{schema:enable-pnets} to building a similar $EnableDataCompLeft$
 ``P>>(Q>>R)'' expression, the corresponding open transition would be:
 
-  \label{OT:example-1}
+  \label{OT:example-2}
         \begin{mathpar}
@@
           \inferrule*[myfraction=\reddottedrule]
-	{\{\xrightarrow{\delta(x3)}_P ~~
-          \xrightarrow{acc(x3)}_Q \} ~~
-          [v_1=0 \land v_2 = 0 \land \forall z. acc(x3) \neq
+	{\{\xrightarrow{\delta(x2)}_P ~~
+          \xrightarrow{acc(x2)}_Q \} ~~
+          [v_1=0 \land v_2 = 0 \land \forall z. acc(x2) \neq
             \delta(z)] ~~ \{v1:=1\}
         }
-	{\ostate{0,0} \xrightarrow {\underline{\delta(x3)}} \ostate{0,0}}
+	{\ostate{0,0} \xrightarrow {\underline{\delta(x2)}} \ostate{0,0}}
 	\end{mathpar}
         where $v_1$ and $v_2$ are respectively the state variables of
-        the first and second Enable2 pNet. Indeed the global
+        the first and second EnableData pNets. Indeed the global
         state space of this version is reduced to $\ostate{0,0}$, and
@@
         \begin{mathpar}
-    ot = \openrule{\{s0 \xrightarrow{fail(true)} s0, t0 \xrightarrow{resume(false)} t0\}, ~~\{\xrightarrow{hb}\},~~fail(true)=fail(b_1)\\
-    \OTland resume(false)=start(b_2)\OTland hb=fail(b_0)\OTland v=\underline{fail}\OTland b_1=b_2\\
-    \OTland (b_1\lor b_2) \Rightarrow b_0, ~~\{\}}
-    	   {\ostate{s0,t0} \xrightarrow{v} \ostate{s0,t0}}
+	  OT_{19}  =
+          \inferrule*[myfraction=\reddottedrule]
+	{\{\xrightarrow{\delta(x2)}_P ~~
+          \xrightarrow{acc(x2)}_R \} ~~
+          [\forall z. \delta(x2) \neq \delta(z) \neq
+            \delta(x2)]
+        }
+	{\ostate{2,0} \xrightarrow {\underline{\delta(x2)}} \ostate{3,0}}
 	\end{mathpar}
-\caption{One of the unsatisfiable open transitions \TODO{to be changed}}  \label{schema:unsat-ot}
+\caption{One of the unsatisfiable open transitions}  \label{schema:unsat-ot}
 \end{figure}
@@
 unsatisfiable open transition 
-from the open automaton of our running example. It shows the case where
+from the open automaton of our running example. \TODO{change the text}It shows the case where
 the failure controller performs a ``$\PortFail$'' action, while the timer
@@
 \IfThenElse {(NonEmptyAssignmentSet($\mathit{L}$))}
-        {\State $\mathit{L1}$=filterUnsatTransitions($\mathit{L,Assignments}$);
-          \State \Return $\mathit{OA}$=makeAutomaton($\mathit{InitState}(P),L)$;}
-        {\State \Return $\mathit{OA}$=makeReachableSubAutomaton($\mathit{InitState}(P),L1)$};
+        {\State \quad\ \Return $\mathit{OA}$=makeAutomaton($\mathit{InitState}(P),L)$;}
+        {\State \quad\ $\mathit{L1}$=filterUnsatTransitions($\mathit{L,Assignments}$);
+         \State \quad\ \Return $\mathit{OA}$=makeReachableSubAutomaton($\mathit{InitState}(P),L1)$};
 \end{algorithmic}  
@@
 in the SMTlib syntax.
-It contains the declaration
+\TODO{Change the text}It contains the declaration
 of the BIP action algebra sorts 
@@
   %  \centerline{\includegraphics[width=12cm]{XFIG/SMTLIB2}}
-    \centerline{\includegraphics[width=\linewidth]{XFIG/SMTLIB3}}
-  \caption{The input of the Z3 solver in SMT-LIB language and the output result\TODO{Change}}  \label{schema:smt-lib}
+    \centerline{\includegraphics[width=0.8\linewidth]{ActaXFIG/rise4fun1}}
+  \caption{Checking one Open Transition in Z3}  \label{schema:smt-lib}
 \end{figure}
@@
 \section{Use-cases}
+\label{section:use-cases}
 \TODO{new section here, showing various features on different examples}
 
-\subsection{Enable operator} in Lotos, with (equivalent) state-based and data-based encodings; Associativity of Enable;
-
-\subsection{simple communication protocol} specification and implementation;
+\subsection{Enable operator} in Lotos, with (equivalent) state-based
+and data-based encodings; Associativity of Enable;
+\label{section:use-case:Enable}
+
+%%\subsection{simple communication protocol} specification and implementation;
 
 \subsection{BIP FailureTimer architecture}
-
 \label{section:FailureTimerMax}
-\label{section:BIParchitectures}
-\label{section:examples}
 
@@
 \noteInEM{Modifications stopped here}
-\label{section:resultTimerInterval}
+\label{section:use-case:Double}
 \TODO{Enhanced FailureTimer, 2 instances composed, with duplicated control and Timer}

### 2019-03-21 2017-Xudong-SMT/ActaInformatica.tex
small TODO editins

@@
 the proof of the finiteness theorem refers to SOS rules Tr1 and
-  Tr2. So maybe we must include (and explain) these here. One problem
-  is that these rules have been modified/improved with each new
-  publication of pNets papers, so we have to decide which version we
-  use here
-    Then we should
-    check if it is sufficient with this version of the algorithm, or
-    if it can be make more precise (some added analysis of the
-    behavior of matching/combining/filetring ?)}
+  Tr2. Yuxin, I agree this proof is NOT required in this paper. But for the
+  sake of reviewing process, (and if I find enough time), I will try
+  to add an appendix with the semantic rules (constructing open
+  transitions from pNets) and the proof of finiteness below }
+
   The possible set of states of the open-automaton is the cartesian
@@
   pNet tree, with a finite number of synchronisation vectors applying
-  at each node the number of global open transition is finite. Similarily rule Tr1 is 
+  at each node the number of global open transitions is finite. Similarily rule Tr1 is 
   applied finitely if the number
@@
 
-\TODO{Candidate theorems: Xudong: state the theorems, and sketch the proofs}
-
-\ERIC{First the good case: if we have no assignments to state variables in
-the system, then we can directly compute the reachable part of the
-automaton using the on-the-fly algorithm.}
+The easy case is when the system does not contain assignments to state
+variables. This does not mean ``data-independancy'': we can still have
+guards in the pLTS transitions and in the synchronisation vectors,
+making the behaviour depending on the value of input variables. But
+the open automaton need not collect the set of possible values deal
+with the values of local variables, so we can directly compute the
+reachable part of the automaton using the on-the-fly algorithm.
 
 \begin{theorem}[Correctness without assignments]
-  \label{Th:finiteness}
+  \label{Th:CorrectnessWithoutAssignments}
 If a pNet contains no assignment to state variables, then the smart
@@
 
-\ERIC{But in presence of assignments, we need to collect all of them
+But in presence of assignments, we need to collect all of them
   before using the assignment information to refine the SAT
   checking. Still, the smart strategy will explore a reduced state
-  space, but not the minimal one (discussion later)}
+  space, but not the minimal one (discussion later).
 
 \begin{theorem}[Correctness without assignments]
-  \label{Th:finiteness}
+  \label{Th:CorrectnessWithAssignments}
 In the general case, then the smart
@@
 \bigl(\PortFail \rightarrow \EX \EU[]{\lnot \PortFail}{
-  \PortReset}\bigr)$.  Additional properties are provided in \ref{TimerRR}.
+  \PortReset}\bigr)$.  Additional properties are provided in \cite{TimerRR}.
 

### 2019-03-21 2017-Xudong-SMT/ActaInformatica.tex
today's end of the day commit...

@@
         In this example we use \emph{synchronised
-          actions}, to express actions that cannot be further synchronised, likesimilar to the
+          actions}, to express actions that cannot be further synchronised, similar to the
         $\tau$ silent action of CCS. We denote them as any action expression with the text
@@
 
+\begin{figure}[~tb]
+\centerline{ 
+  \includegraphics[width=0.30\linewidth]{ActaXFIG/Enable1-aut}
+  \hspace{25mm}
+  \includegraphics[width=0.25\linewidth]{ActaXFIG/Enable2-aut}}
+  \begin{minipage}{5.7cm}
+$  \begin{array}{@{}r@{}l@{}}
+    ot_1  = &\openrule{\{ \xrightarrow{a1}_P \},\\ [\forall x1. a1\neq\delta(x1)]}
+    {A_0 \xrightarrow{a1} A_0}\\
+    ot_2  =& \openrule{
+                            \{\xrightarrow{\delta(x2)}_P,\,
+                            \xrightarrow{acc(x2)}_Q\}  }
+    {A_0 \xrightarrow{\underline{\delta(x2)}} A_1}\\
+    ot_3  =& \openrule{
+                          \{  \xrightarrow{a3}_q \},\\ [\forall x3. a3\neq\delta(x3)] }
+    {A_1 \xrightarrow{a3} A_1}
+  \end{array}$
+  \end{minipage}
+  \hspace{2mm}
+  \begin{minipage}{6cm}
+$  \begin{array}{@{}r@{}l@{}}
+    ot'_1  =& \openrule{
+    	\{\xrightarrow{b1}_P\}, ~~ [\forall y1. b1\neq\delta(y1) \!\land\! v=0]}
+    {B_0 \xrightarrow{b1} B_0}\\
+    ot'_2  =& \openrule{
+                            \{\xrightarrow{\delta(y2)}_P,\,
+                            \xrightarrow{acc(y2)}_Q \}, \\
+                                        v=0, \\
+                                        \{v\gets 1\}}
+    {B_0 \xrightarrow{\underline{\delta(y2)}} B_1}\\
+    ot'_3  =& \openrule{
+                            \xrightarrow{b2}_q, \\ [\forall y2. b2\neq\delta(y2) \!\land\! v=1] }
+    {B_1 \xrightarrow{b2} B_1}
+  \end{array}$
+  \end{minipage}
+  \caption{The two open automata}
+  \label{schema:enable-OAs}
+\end{figure}
+
+The open automata generated for the 2 encodings of Enable in
+Figure~\ref{schema:enable-pnets} are displayed in
+Figure~\ref{schema:enable-OAs}. We have shown in \ref{Forte} how to
+prove that these two automata are bismilar.
+
+Now 
 %%\subsection{simple communication protocol} specification and implementation;

### 2019-03-22 2017-Xudong-SMT/ActaInformatica.tex
big proof read

@@
   \email{eric.madelaine@inria.fr}
+  \qquad
+  \orcid{0000-0002-5552-5993}
 }
@@
 satisfiability of the predicates, and prune the open automaton of its
-unsatisfiable transitions.
-As an industrial oriented use-case, we use so-called ``architectures''
-for BIP systems, that have been used in the framework of an ESA project and to specify the control software of
-a nanosatellite at the EPFL Space Engineering Center. We use pNets to encode a BIP architecture
-extended with explicit data, and compute its
-open automaton semantics. This automaton may be used to prove
-behavioural properties; we give 2 examples, a safety and a liveness
-property.
-\TODO{Add new contrib}
-\todoMargin{Should we remove Min ?}
-\keywords{Networks of Synchronised Automata, Symbolic Behavioral Semantics, Compositional Analysis of Software Components, SMT}
+unsatisfiable transitions. \ERIC{We define and implement an optimized
+algorithm that performs part of the pruning on-the-fly, and show how
+this new algorithm is correct with respect to the original one.
+We illustrate the approach using two use-cases: the first one is a
+classical process-algebra operator for which we provide several
+encodings, and prove basic properties. The second is an industrial
+oriented use-case, based on so-called ``BIP architectures'', that have
+been used in the framework of an ESA project and to specify the
+control software of a nanosatellite at the EPFL Space Engineering
+Center. We use pNets to encode a BIP architecture
+extended with explicit data, compute its semantics and discuss its
+properties, then show how our algorithms scale up, using a
+composition of two such architectures.}
+
+\keywords{Networks of Synchronised Automata, Symbolic Behavioral
+  Semantics, Compositional Analysis of Software Components, SMT} 
 }
@@
   \item $Sorts$ is a set of data \emph{sorts}
-    % \noteSB{Commented out a footnote here\mdash check if still necessary.}
-    %% \footnote{Later we may want to extend this with Sort constructors,
-    %%   like Array or Pair, but this is not needed now}
   \item $\mathit{Constrs}$ is a set of \emph{constructor operators}: for each $\mathit{Con} \in \mathit{Constrs}$, $arity(Con)=n \in \mathbb{N}$ is its arity 
@@
 \subsection{Example}
-\label{section:example}
+\label{section:running-example}
 
@@
 	here a simple example based on the ``Enable'' operator of the LOTOS language.
-	In Fig. \ref{schema:enable-pnets}, we show 2 possible encodings of the  
-	``Enable'' operator.
 	In the Enable expression ``P>>Q'', an \texttt{exit} statement within P
@@
 	is captured by the \texttt{accept} statement of Q. 	
-
 	We use a simple action algebra,
@@
 	possible data type of the variable $x$, corresponding to the
-	statements \texttt{exit} and \texttt{accept}. Both $\delta(x)$
-	and $acc(x)$ actions are
-	implicitly included in the sorts of all processes.
+	statements \texttt{exit} and \texttt{accept}. 
 	We need no specific predicate over the action expressions, apart
 	from equality of actions.
+
+	In Fig. \ref{schema:enable-pnets}, we show 2 possible encodings of the  
+	``Enable'' operator.
         In the first encoding $EnableState$, in the upper part of
@@
 	manner:  the first and third lines represent one vector
-	for each parameterised action in the Sort of hole $P$
+	for each possible action of hole $P$
 	(resp. $Q$). This notation can also use predicates, as in the first
@@
 	composing 2 occurences of the EnableState pNet. In section
-        \ref{section:use-case:Enable} we show how these encodings can
+        \ref{section:use-case:Enable} we will show how these encodings can
         be use to prove properties of the Enable operator.
@@
 The semantics of open pNets will be defined as an open automaton, that
-is an automaton where each transition composes transitions 
+is an automaton where each transition represents the composition transitions 
 of several
@@
 automaton has a set of \emph{state variables} that can be assigned by
-incoming transitions. Strictly speaking, the LTSs at the leaves of the
-open automaton are a restricted form of pLTSs, where labels are
-parametrised actions, but include no guard nor assignments.
+incoming transitions.
+%Strictly speaking, the LTSs at the leaves of the
+%open automaton are a restricted form of pLTSs, where labels are
+%parametrised actions, but include no guard nor assignments.
 
@@
 	\end{mathpar}
-	where $s, s'\in\mathcal{S}$, the $a_i, \beta_j, \alpha$ are
+	where $s, s'\in\mathcal{S}$, the $\beta_j, \alpha$ are
         action expressions,
@@
 
-% \TODO{Relate to the algorithm, or even move to section 5}
 The \emph{states} and the shape of \emph{predicates} in the
@@
   the second vector of its $2^{nd}$ node. Its generated predicate is
-  trivialy true. The global states shows that controler $CState1$ has
-    changed from state 0 to 1.
+  trivialy true. The global states shows that controler $CState1$ is
+    changing from state 0 to 1.
 
@@
 \cite{henrio:Forte2016}, in the form of 2 structural rules, one for
-pLTSs, one for pNet nodes. These rules are slightly improved, adding guards in the synchronisation vectors and syntax for universal quantifier in the guards (see~\cite{Avocs-RR}).
-
-In \cite{henrio:Forte2016} we also proved:
+pLTSs, one for pNet nodes. These rules are slightly improved, adding
+guards in the synchronisation vectors and syntax for universal
+quantifier in the guards (see~\cite{Avocs-RR}).
+
+In \cite{henrio:Forte2016} we also proved the following result, that
+ensure that the termination of our semantic construction algorithm:
 \begin{theorem}[Finiteness]
@@
   sake of reviewing process, (and if I find enough time), I will try
-  to add an appendix with the semantic rules (constructing open
+  to add an appendix with the semantic rules (Tr1 and Tr2, constructing open
   transitions from pNets) and the proof of finiteness below }
@@
   The possible set of states of the open-automaton is the cartesian
-  product of the states of its leaves $pLTS_i^{i\in L}$, that is finite by
+  product of the states of the pNet $pLTS_i^{i\in L}$, that is finite by
   hypothesis. So the top-level residual loop of Algorithm 1 terminates provided each 
@@
 In this section we describe the algorithm implementing the pNet
-semantics, the interaction with the Z3 SMT solver, and we show the
-result on our example. Under the hypotheses of Theorem \ref{Th:finiteness}
-this algorithm terminates.
+semantics, its new ``on-the-fly version, and the interaction with the
+Z3 SMT solver. Under the hypotheses of Theorem \ref{Th:finiteness} 
+both algorithms terminate.
 
@@
 the predicate of each OT is translated 
-into SMTlib assertions, and checked for satisfiability (function \texttt{filterUnsatTransitions}).\\
+into SMTlib assertions (see section~\ref{section:pruning}), and checked for
+satisfiability (function \texttt{filterUnsatTransitions}).\\ 
 Then we compute the set of reachable transitions and states to build
@@
 When applied to a pLTSs at the leaves, we simply take the pLTS transitions of the
-corresponding local state and use the semantic rule to build the OT\footnote{%
+corresponding local state and use the semantic rule to build the OT.
+%\footnote{%
 %
-  We omit detailed presentation of this case for the sake of brevity.
+%  We omit detailed presentation of this case for the sake of brevity.
 %
-}.
+%}.
 When applied to a pNet node we use two methods, combining and
@@
 as shown in Alg.~\ref{alg2}. This method directly manages the
-holes of the node, so \emph{MakeTransitions} is never called on a hole.
-
-%
-%% \noteInSB{Algorithm~\ref{alg2}, as presented below is not
-%%   well-defined: when we reach the leaves, a pLTS does not have any
-%%   subnets, hence the loop in lines 2--4 is empty and so is the list
-%%   $l$. $\mathit{Combining}(l)$ is then called on an empty list...}
-
-%\noteInSB{Line 2: Tr1 and Tr2 are the semantic rules, right?}
-
-%% \noteInSB{Line 6: Nothing in the assignment $\overline{comb} =
-%%   \mathit{Combining}(l)$ depends on $sv$.  Hence, this should probably
-%%   be done outside of the loop.}
-
-%% \noteSB{Line 7: There are two type mismatches here: $ot$ is an open
-%%   transition, whereas $\mathit{Matching}$ is a predicate\mdash one
-%%   cannot assign a predicate to an open transition.  Furthermore, in
-%%   the definition of $\mathit{Matching}$, below, $C_n$ is an open
-%%   transition, whereas $\overline{comb}$ is a {\em set} of open
-%%   transitions, so this call does not type either. There is probably
-%%   another inner loop over all tuples of OTs in $\overline{comb}$; even
-%%   so the open transition has to be defined completely, not just the
-%%   predicate\mdash what is the value of $Post$ for the new transition?
-%%   Maybe $\mathit{Matching}$ should not be a predicate, but an OT?
-%%   Finally, how is $\mathit{hole}$? (I have removed $v$\mdash here and
-%%   in the parameters of the definition of the $\mathit{Matching}$
-%%   predicate, because the text in the paragraph ``Matching'' says that
-%%   $v$ is fresh.)}
-%% \noteEM{Done, please check the new version}
-
-%\noteInSB{Line 8: When is $\mathit{Filter}(ot)$ called?}
+holes of each node, so \emph{MakeTransitions} is never called on a hole.
 
@@
 
-\begin{figure}[t]
-        \begin{mathpar}
-	  OT_{19}  =
-          \inferrule*[myfraction=\reddottedrule]
-	{\{\xrightarrow{\delta(x2)}_P ~~
-          \xrightarrow{acc(x2)}_R \} ~~
-          [\forall z. \delta(x2) \neq \delta(z) \neq
-            \delta(x2)]
-        }
-	{\ostate{2,0} \xrightarrow {\underline{\delta(x2)}} \ostate{3,0}}
-	\end{mathpar}
-\caption{One of the unsatisfiable open transitions}  \label{schema:unsat-ot}
-\end{figure}
-
 Our matching/filtering strategy builds some transitions where
@@
 fragment ``$\mathit{resume}(\false)=\mathit{start}(b_2)$''.
+
+\begin{figure}[h]
+        \begin{mathpar}
+	  OT_{19}  =
+          \inferrule*[myfraction=\reddottedrule]
+	{\{\xrightarrow{\delta(x2)}_P ~~
+          \xrightarrow{acc(x2)}_R \} ~~
+          [\forall z. \delta(x2) \neq \delta(z) \neq
+            \delta(x2)]
+        }
+	{\ostate{2,0} \xrightarrow {\underline{\delta(x2)}} \ostate{3,0}}
+	\end{mathpar}
+\caption{\TODO{Eric: check, it looks wrong}One of the unsatisfiable open transitions}  \label{schema:unsat-ot}
+\end{figure}
 
@@
 \emph{Translation of action algebra presentation.}
-In~\cite{Avocs-RR}, we  define the translation of an algebra presentation into
+In~\cite{AVOCS18}, we  define the translation of an algebra presentation into
 SMTlib declarations (\texttt{declare-datatypes} and
@@
 \label{section:use-cases}
-\TODO{new section here, showing various features on different examples}
-
-\subsection{Enable operator} in Lotos, with (equivalent) state-based
-and data-based encodings; Associativity of Enable;
+In this section we present the result of open automata construction
+for several examples, starting with 3 constructions from
+section~\ref{section:running-example} using the Enable operator.
+Then we give detailed results for the Failure Controler that was
+presented in \cite{AVOCS18}, and show how this sort of BIP Architectures
+can be composed together.
+Finaly we give some figures illustrating the benefits from the smart
+algorithm on these examples.
+
+\subsection{Enable operator} 
 \label{section:use-case:Enable}
 
-\begin{figure}[~tb]
+\begin{figure}[ht]
 \centerline{ 
@@
 Figure~\ref{schema:enable-pnets} are displayed in
-Figure~\ref{schema:enable-OAs}. We have shown in \ref{Forte} how to
+Figure~\ref{schema:enable-OAs}. We have shown in \cite{henrio:Forte2016} how to
 prove that these two automata are bismilar.
@@
 \subsection{BIP FailureTimer architecture}
-\label{section:FailureTimerMax}
+\label{section:FailureTimer}
 
@@
 reset, unless a resumption is registered within $\mathrm{Max}$ time
-units (more details in Sect.~\ref{section:resultOA}).
+units (more details in Sect.~\ref{section:FailureTimer}).
 
@@
 \bigl(\PortFail \rightarrow \EX \EU[]{\lnot \PortFail}{
-  \PortReset}\bigr)$.  Additional properties are provided in \cite{TimerRR}.
+  \PortReset}\bigr)$.  Additional properties are provided in~\cite{Avocs-RR}.
 
@@
 \subsection{Composing 2 FailureTimer BIP Architectures}
-\noteInEM{Modifications stopped here}
 \label{section:use-case:Double}
-\TODO{Enhanced FailureTimer, 2 instances composed, with duplicated control and Timer}
-
-In the conception of the Nano satellite Software \cite[], the Failure
+
+In the conception of the Nano satellite Software \cite{CubETH-case-study}, the Failure
 Timer architecture was used to control several processes
@@
   \centering
-  \includegraphics[width=\columnwidth]{ActaXFIG/BIPspec-DoubleArchFailureTimer-v2-2}
+  \includegraphics[width=0.9\columnwidth]{ActaXFIG/BIPspec-DoubleArchFailureTimer-v2-2}
   \caption{The BIP specification of two composed Failure Monitor architectures}
@@
 
-\begin{figure}[t]
+\begin{figure}[ht]
   \centering
-  \includegraphics[width=\columnwidth]{ActaXFIG/Double-OA}
+  \includegraphics[width=0.9\columnwidth]{ActaXFIG/Double-OA}
   \caption{The resulting automaton}
@@
 
-In each cell of the following table, we display the number of OTs whose predicates were founSAT/UNSAT by the SMT engine, and the overall time spent for the whole algorithm execution.
+In each cell of the following table, we display the number of OTs
+whose predicates were found SAT/UNSAT by the SMT engine, and the overall
+time spent for the whole algorithm execution.
+
+All tests are run on HP xxx laptop under Windows 10 x64, with a Intel quad-Core i7-6600U
+processor, and 32Gb of RAM. The software platform is VerCors
+(https://team.inria.fr/scale/software/vercors/), running on top of
+Eclipse Equinox, with Java 1.8.
 
@@
 		Enable operator   			&
+                3/6 OTs           &
+                3/6 OTs
+                \\\specialrule{0em}{1pt}{1pt} 
+                State-based 		&
+                125 ms 				&
+                110 ms  
+		\\\hline\specialrule{0em}{3pt}{3pt}
+		Enable operator   			&
+                3/6 OTs           &
+                3/6 OTs
+                \\\specialrule{0em}{1pt}{1pt} 
+                Data-based 		&
+                141 ms 				&
+                205 ms  
+		\\\hline\specialrule{0em}{3pt}{3pt}
+		Enable Composition   			&
                 5/55 OTs           &
@@
                 \\\specialrule{0em}{1pt}{1pt} 
-
-                ``(P>Q)>R'' 		&
-                376 ms 				&
-                344 ms  
-		\\\hline\specialrule{0em}{3pt}{3pt}
-		SimpleProt    			&
-                7/260 OTs           &
-                7/57 OTs
-                \\\specialrule{0em}{1pt}{1pt}
-
-                (no holes)&
-                1536 ms 				&
-                359 ms  
+                ``P<<(Q<<R)'' State-based		&
+                359 ms 				&
+                297 ms  
+		%% \\\hline\specialrule{0em}{3pt}{3pt}
+		%% SimpleProt    			&
+                %% 7/260 OTs           &
+                %% 7/57 OTs
+                %% \\\specialrule{0em}{1pt}{1pt}
+
+                %% (no holes)&
+                %% 1536 ms 				&
+                %% 359 ms  
 %                \\\specialrule{0em}{1pt}{1pt}
 %                \textsl{for any sort} & & $=,\ \ne$
-		\\\hline\specialrule{0em}{1pt}{1pt}
-		SimpleProt    			&
-                19/836 OTs           &
-                19/185 OTs
-                \\\specialrule{0em}{1pt}{1pt}
-
-                (with 2 client holes)&
-                2496 ms 				&
-                844 ms  
+		%% \\\hline\specialrule{0em}{1pt}{1pt}
+		%% SimpleProt    			&
+                %% 19/836 OTs           &
+                %% 19/185 OTs
+                %% \\\specialrule{0em}{1pt}{1pt}
+
+                %% (with 2 client holes)&
+                %% 2496 ms 				&
+                %% 844 ms  
 		\\\hline\specialrule{0em}{1pt}{1pt}
@@
                 \\\specialrule{0em}{1pt}{1pt} 
-
   		&
@@
                 \\\specialrule{0em}{1pt}{1pt} 
-
 		&
@@
                 3266 ms  
-
 		\\\hline
@@
 
-        This shows a significant benefit of the ``smart'' strategy, in the considered use-cases, between 30 to 80\% gain depending on the examples.
+        \medskip
+        In the basic cases (EnableState, EnableData) there is no
+        benefit, and even an overhead in the case of EnableData,
+        because of the extra step of checking SAT at the end of the
+        algorithm.
+
+But as soon as there is more that on pLTS in the system and not all
+states are reachable, these tests show a significant benefit of the ``smart'' strategy, in
+the considered use-cases, 50\% for the FailureTimer,
+over to 80\% for the composition, depending
+        on the nature of the examples, but increasing significantly
+        with their complexity.
 
@@
 in term of computing time. We tried a
-slighly bigger example, assembling 2 Failure controllers. In~\cite{Avocs-RR}, we show that Z3 can check the
+slighly bigger example, assembling 2 Failure
+controllers. In~\cite{Avocs-RR}, we show that Z3 can check the 
 satisfiablility of a 90K open transitions in a couple of minutes.

### 2019-03-22 2017-Xudong-SMT/ActaInformatica.tex
changes in English writing

--- 2019-03-21 2017-Xudong-SMT/ActaInformatica.tex
@@
 
-\title{Using an SMT engine to generate Symbolic Automata%
+\title{SMT-Based Generation of Symbolic Automata
 %
@@
 
-\abstract{Open pNets are used to model the behaviour of open systems, both
-synchronous or asynchronous, expressed in various calculi or
-languages. They are endowed with a symbolic operational semantics in
-terms of so-called ``Open Automata''. This allows us to check properties of
+\abstract{Open pNets are formal models that can express the behaviour of open systems, either
+	synchronous, asynchronous, or heterogeneous. They are endowed with a symbolic operational semantics in
+	terms of open automata, which allows us to check properties of
 	such systems in a compositional manner. 
-We implement an algorithm computing these semantics,
-building predicates expressing the synchronization conditions
+	We propose and implement an algorithm computing these semantics,
+	building predicates expressing the synchronisation conditions
 	between the events of the pNet sub-systems. Checking such
-predicates requires symbolic reasoning over first order logics, but
-also over application-specific data. We use the Z3 SMT engine to check
-satisfiability of the predicates, and prune the open automaton of its
-unsatisfiable transitions.
-As an industrial oriented use-case, we use so-called ``architectures''
-for BIP systems, that have been used in the framework of an ESA project and to specify the control software of
-a nanosatellite at the EPFL Space Engineering Center. We use pNets to encode a BIP architecture
-extended with explicit data, and compute its
+	predicates requires symbolic reasoning about first order logics and application-specific data. We use the Z3 SMT engine to check
+	satisfiability of the predicates.
+	%As an industrial oriented use-case, %we use so-called ``architectures''
+	%for BIP systems, that have been used in the framework of an ESA project and to specify the control software of a nanosatellite at the EPFL Space Engineering Center. 
+	We also present several use-cases, in particular, encoding a BIP architecture
+	extended with explicit data and computing its
 	open automaton semantics. This automaton may be used to prove
-behavioural properties; we give 2 examples, a safety and a liveness
-property.
+	behavioural properties such as safety and liveness.
 \TODO{Add new contrib}
 \todoMargin{Should we remove Min ?}
-\keywords{Networks of Synchronised Automata, Symbolic Behavioral Semantics, Compositional Analysis of Software Components, SMT}
+\keywords{pNets, software components, symbolic semantics, SMT
+	%Networks of Synchronised Automata, Symbolic Behavioral Semantics, Compositional Analysis of Software Components, SMT}
 }
@@
 \section{Introduction}
-
 In the nineties, several 
 works extended the basic behavioural models based on labelled
-transition systems to address value-passing or parameterized systems, using
+transition systems to formalise value-passing or parameterised systems, using
 various symbolic encodings of the
 transitions~\cite{deSimone85,Larsen87,HennessyLin:TCS95,Linconcur96}. 
-In \cite{Linconcur96}, H.M. Lin addressed value-passing calculi, for which he
-developed a symbolic behavioural semantics, and proved algebraic properties.
-Separately J. Rathke~\cite{HennessyRathke:TCS98} defined another
+In \cite{Linconcur96}, Lin considered value-passing CCS \cite{Milner89}, for which he
+developed a symbolic behavioural semantics, and developed algorithms for checking symbolic bisimulations.
+Separately, Rathke~\cite{HennessyRathke:TCS98} defined another
 symbolic semantics for 
-a parameterized broadcast calculus, together with strong and weak bisimulation
+a parameterised broadcast calculus, together with strong and weak bisimulation
 equivalences, and developed a symbolic model-checker based on a tableau
-method for these processes. Thirty years later, no
-practical verification approach and no verification platform are
-using this kind of approaches to provide proof methods for
+method for these processes. 
+Later on, symbolic semantics were extended to the $\pi$-calculus \cite{Milner99} and decision algorithms for various symbolic bisimulations were proposed \cite{Li99,Deng2001}. However, no
+practical verification platform has been developed to use this kind of approaches to provide proof methods for
 value-passing processes or open process expressions.
 
-Parameterized Networks of Synchronized Automata (pNets) were proposed
+Parameterised Networks of Synchronised Automata (pNets) were proposed
 to give a behavioural specification formalism for distributed
@@
 verifying distributed systems, as the intermediate language for various
-high-level languages. The high-level languages in VerCors formalize
-each component of the distributed system and their composition.
+high-level languages. The high-level languages in VerCors formalise
+each component of a distributed system and their composition. The model of
 pNets provides the core low-level semantic formalism for VerCors, and
 is made of a hierarchical composition of (value-passing) automata,
-called parameterized labelled transition systems (pLTS), where each
-hierarchical level defines the possible synchronization of the lower levels.
-Traditionally, pNets have been used to formalize fully
+called parameterised labelled transition systems (PLTS), where each
+hierarchical level defines the possible synchronisation of the lower levels.
+Traditionally, pNets have been used to formalise fully
 defined systems or softwares. But we want also to define and reason
@@
 other algebras or  program skeletons.
-The operational semantics of an (open) pNet is defined as an
-Open Automaton in which Open Transitions contain logical predicates
-expressing the relations between the behaviour of the holes, and the
-global behaviour of the system. In the previous publication,
-only a sketch of a procedure allowing to compute these semantics was
+The operational semantics of an open pNet is defined as an
+open automaton in which open transitions contain logical predicates
+expressing the relations between the behaviour of the holes and the
+global behaviour of a system. In previous work,
+only a sketch of a procedure allowing for computing these semantics was
 presented, together with a proof of finiteness of the open automaton, under
@@
 \begin{itemize}
-  \item to get a tool that could be applied to pNets representing
-    various languages, in particular various actions algebras,
-    with their specific decision theories,
+	\item to obtain a tool that could be applied to pNets representing
+	various languages, in particular various action algebras,
+	with their specific decision theories;
 	\item to separate clearly the 
 	algorithm generating the transitions of the open automaton from
-      combination of all possible (symbolic) behaviours, from
+	combination of all possible (symbolic) behaviours, and from
 	the symbolic reasoning part, specifically here using an SMT
 	engine to check the
-      satisfiability of the predicates generated by our algorithm,
+	satisfiability of the predicates generated by our algorithm;
 	\item to build a prototype and validate the approach on our basic
@@
 \paragraph{Contribution}
-In the article we show how:
+In the current work we contribute in the following aspects.
 \begin{itemize}
-\item We define the open automaton generation algorithm. We
-  implemented a full working prototype, within the 
-  VerCors platform. In the process, we improved the
+	\item We present an open automaton generation algorithm. We
+	implement a full working prototype, within the 
+	VerCors platform. In the process, we improve the
 	semantics rules from~\cite{henrio:Forte2016}, and add features in
@@
 	generated by the algorithm.
-    \item \ERIC{we define a strategy checking satisfiability of open transitions in the course the residual algorithm, and show that this ensures that we still generate the reachable part of the open automaton, and that what is generated is minimal with respect to the decidability of predicate satisfiability}
-\item We show the interest of this approach \ERIC{on various use-cases from different settings}, including an
+	\item We define a strategy checking satisfiability of open transitions in the course of the residual algorithm, and show that  the reachable part of the open automaton can be generated and it is minimal with respect to the decidability of predicate satisfiability.
+	\item We show the usage of this approach on various use-cases from different settings, including an
 	industry-inspired case-study, namely one architectural pattern
@@
 %% There is not much research work towards trying 
-Very few attempts were made to develop symbolic bisimulation approaches
-for the value-passing process algebras and languages\mdash our long-term goals\mdash
-especially, there is no algorithmic treatment of the symbolic systems developed by
+As mentioned above, early attempts were made by Lin and others to define symbolic bisimulations for process calculi such as value-passing CCS and the $\pi$-calculus, and design algorithms to compute the most general condition under which two processes are bisimilar.
+However, there is no algorithmic treatment of the symbolic systems developed by
 interacting with automatic theorem provers. The closest work is the
-one already mentioned from J. Rathke~\cite{HennessyRathke:TCS98},
+one already mentioned by Rathke~\cite{HennessyRathke:TCS98},
 who developed the symbolic bisimulation for a
-calculus of broadcasting system (CBS). CBS is similar with classic
+calculus of broadcasting system (CBS). CBS is similar to classic
 process calculi such as CCS and CSP, but communicating by broadcasting
@@
 \paragraph{Structure.}
-In section
+In Section
 \ref{section:pnets} we give a description and a formal definition of
-the pNet model, as found in previous publications, and present a
-running example based on Lotos ``Enable'' operator.
-Section \ref{section:op-semantics} recalls briefly the operational semantics
-of pNet.
-Section \ref{section:implementation} explains in details the algorithm
-used to compute this semantics, including the interaction with Z3, and
-shows the full result of the semantic computation on the running
-example.
-In section \ref{section:use-cases} we show the result of the study of
-our running example, then explain a bigger use-case based on a BIP
-architecture from the nano-satellite case-study. We show the benefits
-drawn from the smart algorithm.
+the pNet model. 
+In Section \ref{section:op-semantics} we briefly recall  the operational semantics
+of pNets.
+In Section \ref{section:implementation} we present an algorithm to compute this semantics, including the interaction with Z3.
+In Section~\ref{sec:cases} we give a few use-cases, in particular, a BIP
+architecture from the nano-satellite case-study. 
 Finally we conclude and discuss perspectives in Section
@@
 
-\section{Background: pNets definition}
+\section{Preliminaries}
 \label{section:pnets}
 
-This section introduces pNets and the notations we will use in
-this paper. Then it gives the formal definition of pNet structures,
-together with an operational semantics for open pNets.
-
-pNets are tree-like structures, where the leaves are either
-\emph{parameterized labelled transition systems (pLTSs)}, expressing the
+We first introduce pNets and some notations, then give the formal definition of pNet structures, together with an operational semantics for open pNets.
+
+A pNet has a tree-like structure, where the leaves are either
+\emph{parameterised labelled transition systems (PLTSs)}, expressing the
 behaviour of basic processes, or \emph{holes}, used as placeholders
@@
 %follows:
-$a_i^{i\in I}$
+The symbol $a_i^{i\in I}$
 denotes a family of elements $a_i$ indexed over the
 set $I$.
-When this is not
-ambiguous, we shall use notations for sets, and typically write
-``indexed set over I'' when formally we should speak of multisets, and
-write $x\in a_i^{i\in I}$ to mean $\exists i\in I.\, x=a_i$.  An empty
-family is denoted $\emptyset$. We
+When this is unambiguous, we shall use notations for sets, and typically write
+``indexed sets over I'' which formally means multisets, and
+write $x\in a_i^{i\in I}$ to mean $x=a_i$ for some $i\in I$.  An empty
+family is written $\emptyset$. We
 denote classically $\overline{a}$ a family when the indexing set is
-irrelevant.  $\uplus$ is the disjoint union on indexed sets.
-
-\paragraph*{Term algebra.}
-Our models rely on a notion of parameterized actions that are
+irrelevant. The symbol $\uplus$ stands for the disjoint union of indexed sets.
+
+\paragraph*{Term algebra.} \
+Our models rely on a notion of parameterised actions that are
 symbolic expressions using data types and variables. As we want to encode
 the low-level behaviour of possibly very different
-programming languages, we do not want to impose one specific algebra
+programming languages, we do not impose one specific algebra
 for denoting actions, nor any specific communication mechanism. So we
@@
 	\begin{itemize}
-  \item $Sorts$ is a set of data \emph{sorts}
+		\item $Sorts$ is a set of data sorts.
 		% \noteSB{Commented out a footnote here\mdash check if still necessary.}
@@
 		arity and signature, of the form: $Op : \mathit{sort}_1, \dots,  \mathit{sort}_n \rightarrow
-      \mathit{sort}$
+		\mathit{sort}$.
 		\item $\mathit{Constrs}(\mathit{sortname})$ and $\mathit{Sels}(\mathit{sortname})$ are, respectively, the sets of
-        constructors and selectors of the sort $\mathit{sortname}$
+		constructors and selectors of the sort $\mathit{sortname}$.
 	\end{itemize}
@@
 		\\\hline\specialrule{0em}{1pt}{1pt}
-\multicolumn{3}{l}{\sl Extension for the BIP use-case of Fig.~\ref{schema:ArchFailure:pNet}}
+		\multicolumn{3}{l}{\sl Extension for the BIP use-case of Figure~\ref{schema:ArchFailure:pNet}}
 		\\\hline\specialrule{0em}{1pt}{1pt}
@@
 
-\subsection{The (open) pNets Core Model}
+\subsection{The (Open) pNets Core Model}
 \label{section:pNets}
 
-A pLTS is a labelled transition system with variables, which can be
+A PLTS is a labelled transition system with variables, which can be
 manipulated, defined, or accessed inside states, actions, guards, and
@@
 
-\begin{definition}[pLTS]
-\label{pLTS}
+\begin{definition}[PLTS]
+	\label{PLTS}
 	%\noteSB{It's a bit strange that algebra presentations are not referred to here}
-Given a term algebra $\Talg$, a pLTS is a tuple
-$pLTS\triangleq\mylangle S,s_0, \to\myrangle$ where:
+	Given a term algebra $\Talg$, a PLTS is a tuple
+	$PLTS\triangleq\mylangle S,s_0, \to\myrangle$ where:
 	\begin{itemize}
@@
 		$\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in J}\rangle$,
-  where $\alpha \in\AlgA_{\P}$ is a parameterized action,
+		where $\alpha \in\AlgA_{\P}$ is a parameterised action,
 		$e_b \in \AlgB_{\P}$ is a guard, and
@@
 %% the sub-pNets.
-The relation between actions of a pNet and those of its sub-pNets
+The relation between the actions of a pNet and those of its sub-pNets
 %% internal actions is
-are given by  \emph{synchronization vectors}, which %% : a
-%% synchronization vector 
-synchronize one or several internal actions, and
+is given by  \emph{synchronisation vectors}, which %% : a
+%% synchronisation vector 
+synchronise one or several internal actions, and
 expose a single resulting global action.
@@
 \begin{definition}[pNets]\label{def-pnets}
-    A pNet is a hierarchical structure where leaves are pLTSs and holes:
+	A pNet is a hierarchical structure where leaves are PLTSs and holes:
 	%%  \footnote{Typing can 
@@
 	%% sort~\cite{HMZ-FORTE2016}}
-$\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, J, \symb{SV}_k^{k\in 
+	$\pNet\triangleq PLTS~|~\mylangle \pNet_i^{i\in I}, J, \symb{SV}_k^{k\in 
 		K}\myrangle$, with $I, J, K$ potentialy infinite,
@@
 here a simple example based on the ``Enable'' operator of the LOTOS language.
-	In Fig. \ref{schema:enable-pnets}, we show 2 possible encodings of the  
+In Figure \ref{schema:enable-pnets}, we show two possible encodings of the  
 ``Enable'' operator.
-	In the Enable expression ``P>>Q'', an \texttt{exit} statement within P
+In the Enable expression ``P>>Q'', an \texttt{exit(x)} statement within P
 terminates the current process, carrying a value $x$ that
-	is captured by the \texttt{accept} statement of Q.
+is captured by the \texttt{accept(x)} statement of Q.
 
@@
 possible data type of the variable $x$, corresponding to the
-	statements \texttt{exit} and \texttt{accept}. Both $\delta(x)$
+statements \texttt{exit(x)} and \texttt{accept(x)}. Both $\delta(x)$
 and $acc(x)$ actions are
@@
 from equality of actions. 
-	In the first encoding $EnableState$, in the upper part of
-	Fig. \ref{schema:enable-pnets}, we use a controller $CState$ with two
+In the first encoding $Enable1$, in the upper part of
+Figure \ref{schema:enable-pnets}, we use a controller $C_1$ with two
 states, and simple control actions $l, r, \delta$. The second encoding
-	$EnableData$ uses a data-oriented style, with a single state controller $CData$, and a
-	state-variable $v$, with values in $\{0,1\}$.
+$Enable2$ uses a data-oriented style, with a single state controller, and a
+state-variable $s_0$, with values in $\{0,1\}$.
 
 In this example we use \emph{synchronised
-          actions}, to express actions that cannot be further synchronised, similar to the
-        $\tau$ silent action of CCS. We denote them as any action expression with the text
+	actions}, to express actions that cannot be further synchronised, like the
+silent action $\tau$ of CCS. We denote them as any action expression with the text
 underlined, as e.g. $\underline{\delta(x_2)}$. Such
-        synchronised actions do not play any special role for defining
+actions do not play any special role for defining
 the semantics of pNets, but as one can expect, will be crucial
@@
 
-	In Fig. \ref{schema:enable-composed}, we enrich our example by
-	composing 2 occurences of the EnableState pNet. In section
-        \ref{section:use-case:Enable} we show how these encodings can
-        be use to prove properties of the Enable operator.
-
-\section{Operational Semantics for Open pNets}
+In Figure \ref{schema:enable-composed}, we enrich our example by
+composing two occurences of the EnableState pNet. %For simplicity, we only represent one instance of the synchronisation vector set, and of the controller.
+In Section~\ref{section:use-case:Enable} we show how these encodings can
+        be used to prove properties of the Enable operator.
+
+\section{Operational Semantics of Open pNets}
 \label{section:op-semantics}
@@
 incoming transitions. Strictly speaking, the LTSs at the leaves of the
-open automaton are a restricted form of pLTSs, where labels are
-parametrised actions, but include no guard nor assignments.
+open automaton are a restricted form of PLTSs, where labels are
+parametrised actions, but include neither guard nor assignments.
 
@@
 	% a set  $\langle S_i,s_{0 i}, \rightarrow_i\rangle^{i\in I}$ of LTSs,
-        a set $J$ of holes, %with sorts $Sort_j^{j\in J}$
+	a set $J$ of holes %with sorts $Sort_j^{j\in J}$
 	and a set of states $\mathcal{S}$ is a structure of the form:	
@@
 	substitution $\{x_k\gets e_k\}^{k\in K}$  
-	where $x_k$ are variables of $s'$ and $s'_i$, whereas $e_k$ are
-        expressions over the other variables of the open transition.
+	where $x_k$ is a variable of $s'$ or $s'_i$, whereas $e_k$ is an
+	expression over other variables of the open transition.
 \end{definition}
@@
 in structured states as $\triangleleft\ldots\triangleright$).
-  For any pNet p, let $\overline{\mathit{Leaves}} = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be the set of pLTS at its leaves,
+For any pNet p, let $\overline{\mathit{Leaves}} = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be the set of PLTSs at its leaves,
 then $\mathit{States}(p) = \{\ostate{s_i^{i\in L}}
 |\, \forall i\in L. s_i \in S_i\}$.
-A pLTS being its own single leave:
+A PLTS could be its own single leave:
 $\mathit{States}(\mylangle S,s_0, \to\myrangle) = \{\ostate{s}|\, s \in S\}$.
@@
   Transition $OT_1$ of the pNet $EnableStateCompLeft$ is generated by
-  combination of the first vector of its root node, with
-  the second vector of its $2^{nd}$ node. Its generated predicate is
-  trivialy true. The global states shows that controler $CState1$ has
+  combining the first vector of its root node with
+  the second vector of its second node. Its generated predicate is
+  trivially true. The global states shows that controler $CState1$ has
     changed from state 0 to 1.
@@
 If we use the data-oriented pNet $EnableData$ from Figure
-\ref{schema:enable-pnets} to building a similar $EnableDataCompLeft$
+\ref{schema:enable-pnets} to build a similar $EnableDataCompLeft$
 ``P>>(Q>>R)'' expression, the corresponding open transition would be:
@@
 \paragraph{Structural Semantic Rules:}
-The semantics of pNet in term of open automata has been defined in
-\cite{henrio:Forte2016}, in the form of 2 structural rules, one for
-pLTSs, one for pNet nodes. These rules are slightly improved, adding guards in the synchronisation vectors and syntax for universal quantifier in the guards (see~\cite{Avocs-RR}).
+The semantics of pNet in terms of open automata has been defined in
+\cite{henrio:Forte2016}, in the form of two structural rules, one for
+pLTSs, and the other for pNet nodes. These rules are slightly improved, adding guards in the synchronisation vectors and syntax for universal quantifier in the guards (see~\cite{Avocs-RR}).
 
@@
   \label{Th:finiteness}
-  Given an open pNet $pnet=\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $l_i^{i\in I}$ and holes $h_j^{j\in
-  J}$, if the sets $I$ and $J$ are finite, if the synchronisation vectors of all pNets 
-  included in  $pnet$   are finite, and if
-$\forall i \in L.\, finite{(states(l_i))} \text{ and } l_i$
-has a finite number of state variables, then its semantics is an open automaton 
-$\mathcal{T}$ with finitely many states and transitions.
+   Let $pnet=\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ be an open pNet  with leaves $l_i^{i\in I}$ and holes $h_j^{j\in
+ 	J}$, where the sets $I$ and $J$ are finite. Suppose the synchronisation vectors of all pNets 
+ included in  $pnet$   are finite, and 
+ % $\forall i \in L.\, finite{(states(l_i))} \text{ and } l_i$ 
+ $l_i $ has a finite number of state variables for each $i\in I$. Then the semantics of $pnet$ is an open automaton 
+ %$\mathcal{T}$ 
+ with finitely many states and transitions.
 \end{theorem}
-  Remark that all the elements of such pNets and open automata being
-symbolic, they can represent many classes of unbounded systems.
+  Remark that all the elements of such pNets and open automata are symbolic, and they can represent many classes of unbounded systems.
 
@@
 \ERIC{Before the SAT checking step, it may contain symbolic transitions that
-do not have valid ground instanciations. This is not logicaly
+do not have valid ground instanciations. This is not logically
 incorrect, but is naturaly not an optimal representation. So we prune
@@
 the predicate of each OT is translated 
-into SMTlib assertions, and checked for satisfiability (function \texttt{filterUnsatTransitions}).\\
+into SMTlib assertions, and checked for satisfiability (function \texttt{filterUnsatTransitions}).
 Then we compute the set of reachable transitions and states to build
@@
 the semantic rules following the structure of the pNet.
-When applied to a pLTSs at the leaves, we simply take the pLTS transitions of the
+When applying a rule to a PLTS at the leaves, we simply take the PLTS transitions of the
 corresponding local state and use the semantic rule to build the OT\footnote{%
@@
 Here, we only detail the construction of the predicate.
-From a synchronization vector
-$sv = \left((a'_i)^{i\in I} (b'_j)^{j\in J}\rightarrow v'\right) \in SV$
-and its guard $G_k$; a tuple of open transitions
-$C = ({ot}_i)^{i \in [1,n]} \in \overline{comb}$, such that, for each $i \in [1,n]$, either $ot_i = -$, or the result action of $ot_i$ is $a_i$; the hole behaviours $\mathit{Hole} = (b_j)^{j \in J}$; and a fresh variable $v$, representing the result action of the OT under construction, we build the predicate:
+Suppose that $sv = \left((a'_i)^{i\in I} (b'_j)^{j\in J}\rightarrow v'\right) \in SV$ is a synchronisation vector, $G_k$ is its guard, and
+$C = ({ot}_i)^{i \in [1,n]} \in \overline{comb}$ is a tuple of open transitions such that, for each $i \in [1,n]$, either $ot_i = -$, or the result action of $ot_i$ is $a_i$.
+Suppose futher that $\mathit{hole} = (b_j)^{j \in J}$ is the hole behaviour and $v$ is a fresh variable, representing the result action of the OT under construction.
+Then we can  build the predicate:
 %
@@
 unification  will be checked later, together with the guards collected
-from synchronisation vectors and from pLTS transtions, using the
+from synchronisation vectors and from PLTS transtions, using the
 satisfiability check in the SMT engine.
 
-\subsection{Management of state variable assignments}
-
-In a pLTS, there may be several incoming transitions 
+\subsection{Management of State Variable Assignments}
+
+In a PLTS, there may be several incoming transitions 
 that assign potentially different (symbolic) values to a state variable.
 To handle such cases, the algorithm manages a
-list of assignment expressions for each pLTS state. 
-\QIN{The only assignments happen on state variables, at pLTS level: every time the MakeTransitions
-algorithm is applied on a pLTS, it collects the expressions from the $Post$ in each transition.
+list of assignment expressions for each PLTS state. 
+\QIN{The only assignments for state variables that happen at the PLTS level are as follows: every time the MakeTransitions
+algorithm is applied on a PLTS, it collects the expressions from the $Post$ in each transition.
 % As there is no assignments collecting work on a pNet node, it is not
@@
 is the disjoint union
-of sets of state variables of the individual pLTS states constituting this
+of sets of state variables of the individual PLTS states constituting this
 global state. \ERIC{The final assignment sets are assembled when building the
@@
 
-\subsection{Pruning the unsatisfiable results}
+\subsection{Pruning the Unsatisfiable Results}
 \label{section:pruning}
@@
 transitions and states), by checking the predicates for satisfiability.
-In Fig.~\ref{schema:unsat-ot}, we show an 
+In Figure~\ref{schema:unsat-ot}, we show an 
 unsatisfiable open transition 
@@
 may depend on the specific theory of the action algebra datatypes. 
-The ``Modulo Theory'' part of SMT solvers is important here, so that
-the solver can use specific properties of each action algebra.
-
-\subsection{Computing reachable state space on the fly}
-
-\ERIC{The basic algorithm from the previous section potentialy explores some
+The ``Modulo Theory'' part of SMT solvers is important here, as
+the solvers can use specific properties of each action algebra.
+
+\subsection{Computing Reachable State Space on the Fly}
+
+\ERIC{The basic algorithm from the previous section potentially explores some
 areas of the global state-space that will not be reachable after
@@
 first step, the SAT checking is done without using any assignment set
-information. Then after completion of this step, we perform another
+information. Then after the completion of this step, we perform another
 SAT checking of all transitions from step1, but this time using the
 assignment information. This may reduce the reachable state space. If
-we want to be sure the obtained automaton is minimal, we should
-iterate this step until a fix-point is reached. But in practical cases, very
+we want to be sure that the obtained automaton is minimal, we should
+iterate this step until a fixed point is reached. But in practical cases, very
 little will be gained, so the default implementation does only one
 step. Leaving some UNSAT transitions in the
-symbolic automaton is still logicaly correct.
+symbolic automaton is still logically correct.
 
@@
   or id the explanation above sufficient ?}
+{\color{green} Yuxin: I think the explanation above is sufficient. What's more important is to give formal proofs for the three theorems.}
 
@@
 
-Algorithm~\ref{alg3} implement this new stategy: in line 5, it runs
+Algorithm~\ref{alg3} implements this new stategy: in line 5, it runs
 the satisfiability check on each OT generated from this global
@@
 
-Then at the end of the residual loop, we do another traversal of the
+At the end of the residual loop, we do another traversal of the
 automaton, this time using the assignment information collected that
-far, and compute the final reachable sub-automaton. This step,
-naturaly, is only useful if there are some assignments.
+far, and compute the final reachable sub-automaton. 
+Naturally, this step is only useful if there are some assignments.
 
 The easy case is when the system does not contain assignments to state
-variables. This does not mean ``data-independancy'': we can still have
-guards in the pLTS transitions and in the synchronisation vectors,
+variables. This does not mean ``data-independency'': we can still have
+guards in the PLTS transitions and in the synchronisation vectors,
 making the behaviour depending on the value of input variables. But
-the open automaton need not collect the set of possible values deal
+the open automaton need not to collect the set of possible values dealing
 with the values of local variables, so we can directly compute the
@@
 algorithm, without final reachability computation, computes exactly
-the same open automaton as algorithm 1.
+the same open automaton as Algorithm 1.
   \end{theorem}
@@
 
-But in presence of assignments, we need to collect all of them
+But in the presence of assignments, we need to collect all of them
   before using the assignment information to refine the SAT
   checking. Still, the smart strategy will explore a reduced state
-  space, but not the minimal one (discussion later).
+  space, not necessarily the minimal one (discussion later).
 
@@
   \label{Th:CorrectnessWithAssignments}
-In the general case, then the smart
+In the general case, the smart
 algorithm, with a final reachability computation, computes exactly
-the same open automaton as algorithm 1.
+the same open automaton as Algorithm 1.
 \end{theorem}
@@
 particular because of structured names for the fresh variables generated
-by the algorithm, allowing tracability of the result~\cite{Avocs-RR}.
-
-Figure~\ref{schema:smt-lib} shows the translation of the
-transition of Fig.~\ref{schema:unsat-ot}
+by the algorithm, allowing for tracability of the result~\cite{Avocs-RR}.
+
+Figure~\ref{schema:smt-lib} shows the translation of  Figure~\ref{schema:unsat-ot}
 in the SMTlib syntax.
@@
 a synchronisation vector has imposed on the behavior of ``B''.
-Here we display also the diagnosis (``sat'' or ``unsat'') generated by Z3.
+We also display  the diagnosis (``sat'' or ``unsat'') generated by Z3.
 
@@
 
-By lack of space, we have only shown here a use-case with boolean data
+For simplicity, we have only shown here a use-case with boolean data
 parameters, so we only require the basic SAT capability of the Z3
 engine. It should be clear that more involved examples will require
-reasonning on predicates of various data types. Z3 provides theories for reasonning
-on integers, bitstrings, enumerated types, arrays, etc.
+reasoning about predicates of various data types. Z3 provides theories for reasonning
+about integers, bitstrings, enumerated types, arrays, etc.
 We also need to deal with some universal quantification on free
-variables occuring in the guards of synch vectors.
-For other data structures usual in such models, like records, or
+variables occuring in the guards of synchronisation vectors.
+For other data structures  in such models, like records, or
 recursive structures, the user will have to develop its own theories.
-Decidability of these theories will condition the completeness of the
+Decidability of these theories will condition on the completeness of the
 satisfiability check, and the decidability of model-checking or
@@
 SMTlib declarations (\texttt{declare-datatypes} and
-\texttt{declare-fun}). We also formalize a condition of well-formedness of pNets ensures that the generated code is correct,
+\texttt{declare-fun}). We also formalise a condition of well-formedness of pNets to ensure that the generated code is correct,
 and will not raise runtime errors in the SMT engine. Note that the
 \texttt{declare-datatypes} command comprises both the action
-constructors from table \ref{table:BIPalgebra} and also the constant action
+constructors from Table~\ref{table:BIPalgebra} and also the constant action
 names from our example.
@@
 \begin{itemize}
-\item collect all variables in the transition, and declare them (using \texttt{declare-const})
-\item check well-formedness and correct typing of expressions,
-\item translate the predicate into a conjunction of assertions,
-\item if present in the source state, translate the state-variable
-  assignments into a disjunctive assertion.
+	\item to collect all variables in the transition, and declare them (using \texttt{declare-const})
+	\item to check the well-formedness and correct typing of expressions,
+	\item to translate the predicate into a conjunction of assertions,
+	\item to translate the state-variable
+	assignments into a disjunctive assertion, if the assignments are present in the source state.
 \end{itemize}
@@
 
-\section{Use-cases}
+\section{Use-Cases}
 \label{section:use-cases}
@@
 
-\subsection{Enable operator} in Lotos, with (equivalent) state-based
+\subsection{Enable Operator} in Lotos, with (equivalent) state-based
 and data-based encodings; Associativity of Enable;
@@
 
-\subsection{BIP FailureTimer architecture}
+\subsection{BIP FailureTimer Architecture}
 \label{section:FailureTimerMax}
@@
 the ports of the corresponding components, Boolean guards and update
-functions on local variables.  For instance the loop transition
+functions on local variables.  For instance, the loop transition
 $t_1 \goesto{\PortTick, [t < Max], t:=t+1} t_1$
-in the $\NameTimer$ component is labeled by the port $\PortTick$, it
+in the $\NameTimer$ component is labelled by the port $\PortTick$. It
 can be fired only when the current value of the local variable $t$ is
@@
 attributes of the connected ports~\cite{BliSif08-acp-tc}, which may be
-either \emph{trigger} (triangles in Fig.~\ref{schema:ArchFailure:BIP})
-or \emph{synchron} (bullets in Fig.~\ref{schema:ArchFailure:BIP}).
+either \emph{triggers} (triangles in Figure~\ref{schema:ArchFailure:BIP})
+or \emph{synchrons} (bullets in Figure~\ref{schema:ArchFailure:BIP}).
 %
-If all sub-connectors of a connector are synchrons, then an
+If all the sub-connectors of a connector are synchrons, then an
 interaction may be executed by the connector only if each subconnector
@@
 %
-For instance, the two ports $\NameTimer.start$ and
+For instance, the two ports $\NameTimer.\PortStart$ and
 $\NameCtrl.\PortFail$ are always synchronised, since they belong to
@@
 above Failure Monitor architecture.  This encoding is structural: each
-coordinator component is encoded as a pLTS, the operand
-component\mdash as a hole; connectors of the BIP model are encoded as
+coordinator component is encoded as a PLTS and the operand
+component as a hole; connectors of the BIP model are encoded as
 synchronisation vectors.  Each connector that does not involve
@@
 value to each of these ports: the original transitions carry the value
-$\true$ (\eg $c_0 \goesto{\PortFail(\true)} c_1$), the
+$\true$ (\eg $c_0 \goesto{\PortFail(\true)} c_1$) and the
 added loops carry the value $\false$ (\eg $c_2
@@
 3 reachable global states (out of the possible 6) and 10 open
-transitions, is shown in Fig.~\ref{schema:resultOA1}.
+transitions, is shown in Figure~\ref{schema:resultOA1}.
 
@@
 
-\subsection{Composing 2 FailureTimer BIP Architectures}
+\subsection{Composing Two FailureTimer BIP Architectures}
 \noteInEM{Modifications stopped here}
@@
 
-In the conception of the Nano satellite Software \cite[], the Failure
-Timer architecture was used to control several processes
+In the conception of the nanosatellite software \cite[], the FailureTimer architecture was used to control several processes
 communicating on the common bus. Timeout signals (``$ask$''), resets,
@@
 In Figure~\ref{schema:ArchFailure:Double:OA} we show the resulting
-open automaton. Remark that it shows that th etwo timers are forced to
+open automaton. It indicates that the two timers are forced to
 be synchronous: each can only tick after the other has also started,
@@
 
-\subsection{Benefits from the Smart algorithm}
-
-In each cell of the following table, we display the number of OTs whose predicates were founSAT/UNSAT by the SMT engine, and the overall time spent for the whole algorithm execution.
+\subsection{Benefits from the Smart Algorithm}
+
+In each cell of the following table, we display the number of OTs whose predicates were founSAT/UNSAT by the SMT engine, and the overall time spent for the execution of the whole algorithm.
 
@@
 
-        This shows a significant benefit of the ``smart'' strategy, in the considered use-cases, between 30 to 80\% gain depending on the examples.
+        This shows a significant benefit of the ``smart'' strategy, in the considered use-cases, between 30\% and 80\% gain depending on the examples.
 
@@
 The formal definitions and properties of the open pNets model were
-published in \cite{henrio:Forte2016}. In this new work we describe an implementation of
+given in \cite{henrio:Forte2016}. In the current work we describe an implementation of
 the model and its semantics construction, including its interaction
 with the Z3 SMT engine.
-The implementation has two parts: the first is a finitary algorithm
+The implementation has two parts: the first is an algorithm
 that builds all possible combinations of synchronisations through the
 pNet hierarchical structure. The result is a so-called
-\emph{open-automaton}, which transitions contains predicates relating
+\emph{open automaton}, whose transitions contain predicates relating
 the actions of the pNet holes and controllers. Some of the open
-transitions obtained at this step,  may
+transitions obtained at this step  may
 contain predicates which do not represent any possible concrete
 instantiations. 
-In the second part of the tool we use the SMT solver Z3 for checking the
+In the second part of the tool we use the SMT solver Z3 to check the
 satisfiability of the predicate in each open transition. 

### 2019-03-23 2017-Xudong-SMT/ActaInformatica.tex

@@
 	%for BIP systems, that have been used in the framework of an ESA project and to specify the control software of a nanosatellite at the EPFL Space Engineering Center. 
-	We also present several use-cases, in particular, encoding a BIP architecture
-	extended with explicit data and computing its
-	open automaton semantics. This automaton may be used to prove
-	behavioural properties such as safety and liveness.
+%	We also present several use-cases, in particular, encoding a BIP architecture
+%	extended with explicit data and computing its
+%	open automaton semantics. This automaton may be used to prove
+%	behavioural properties such as safety and liveness.
+\ERIC{We also propose and implement an optimised
+	algorithm that performs part of the pruning on-the-fly, and show how
+	this new algorithm is correct with respect to the original one.
+	We illustrate the approach using two use-cases: the first one is a
+	classical process-algebra operator for which we provide several
+	encodings, and prove basic properties. The second is  industry-oriented and based on the so-called ``BIP architectures'', which have
+	been used to specify the
+	control software of a nanosatellite at the EPFL Space Engineering
+	Center. We use pNets to encode a BIP architecture
+	extended with explicit data, compute its semantics and discuss its
+	properties, and then show how our algorithms scale up, using a
+	composition of two such architectures.}}
+
 \TODO{Add new contrib}
@@
 	here a simple example based on the ``Enable'' operator of the LOTOS language.
-In Figure \ref{schema:enable-pnets}, we show two possible encodings of the  
-``Enable'' operator.
-In the Enable expression ``P>>Q'', an \texttt{exit(x)} statement within P
+	In the Enable expression ``P>>Q'', an \texttt{exit} statement within P
 	terminates the current process, carrying a value $x$ that
-is captured by the \texttt{accept(x)} statement of Q.
-
+	is captured by the \texttt{accept} statement of Q. 	
 	We use a simple action algebra,
@@
 	possible data type of the variable $x$, corresponding to the
-statements \texttt{exit(x)} and \texttt{accept(x)}. Both $\delta(x)$
-and $acc(x)$ actions are
-implicitly included in the sorts of all processes.
+	statements \texttt{exit} and \texttt{accept}. 
 	We need no specific predicate over the action expressions, apart
 	from equality of actions.
-In the first encoding $Enable1$, in the upper part of
-Figure \ref{schema:enable-pnets}, we use a controller $C_1$ with two
+
+	In Figure \ref{schema:enable-pnets}, we show two possible encodings of the  
+	``Enable'' operator.
+        In the first encoding $EnableState$, in the upper part of
+	Figure \ref{schema:enable-pnets}, we use a controller $CState$ with two
 	states, and simple control actions $l, r, \delta$. The second encoding
-$Enable2$ uses a data-oriented style, with a single state controller, and a
-state-variable $s_0$, with values in $\{0,1\}$.
+	$EnableData$ uses a data-oriented style, with a single state controller $CData$, and a
+	state-variable $v$, with values in $\{0,1\}$.
 
         In this example we use \emph{synchronised
-	actions}, to express actions that cannot be further synchronised, like the
+          actions}, to express actions that cannot be further synchronised, similar to the
          silent action $\tau$ of CCS. We denote them as any action expression with the text
         underlined, as e.g. $\underline{\delta(x_2)}$. Such
-actions do not play any special role for defining
+        synchronised actions do not play any special role for defining
         the semantics of pNets, but as one can expect, will be crucial
@@
 	manner:  the first and third lines represent one vector
-for each parameterised action in the Sort of hole $P$
+	for each possible action of hole $P$
 	(resp. $Q$). This notation can also use predicates, as in the first
@@
 	In Figure \ref{schema:enable-composed}, we enrich our example by
-composing two occurences of the EnableState pNet. %For simplicity, we only represent one instance of the synchronisation vector set, and of the controller.
-In Section~\ref{section:use-case:Enable} we show how these encodings can
+	composing two occurences of the EnableState pNet. In Section
+        \ref{section:use-case:Enable} we will show how these encodings can
         be used to prove properties of the Enable operator.
@@
 automaton has a set of \emph{state variables} that can be assigned by
-incoming transitions. Strictly speaking, the LTSs at the leaves of the
-open automaton are a restricted form of PLTSs, where labels are
-parametrised actions, but include neither guard nor assignments.
+incoming transitions.
+%Strictly speaking, the LTSs at the leaves of the
+%open automaton are a restricted form of pLTSs, where labels are
+%parametrised actions, but include no guard nor assignments.
 
@@
 \end{definition}
-
 %
@@
   the second vector of its second node. Its generated predicate is
-  trivially true. The global states shows that controler $CState1$ has
-    changed from state 0 to 1.
-
+  trivially true. The global states show that controler $CState1$ is
+  changing from state 0 to 1.
   \label{OT:example-1}
@@
 \paragraph{Structural Semantic Rules:}
-The semantics of pNet in terms of open automata has been defined in
+The semantics of pNets in terms of open automata has been defined in
 \cite{henrio:Forte2016}, in the form of two structural rules, one for
-pLTSs, and the other for pNet nodes. These rules are slightly improved, adding guards in the synchronisation vectors and syntax for universal quantifier in the guards (see~\cite{Avocs-RR}).
-
-In \cite{henrio:Forte2016} we also proved:
+PLTSs, and the other for pNet nodes. These rules are slightly improved, adding guards in the synchronisation vectors and syntax for universal quantifier in the guards (see~\cite{Avocs-RR}).
+
+In \cite{henrio:Forte2016} we also proved the following result, that
+ensure that the termination of our semantic construction algorithm:
 \begin{theorem}[Finiteness]
@@
 In this section we describe the algorithm implementing the pNet
-semantics and the interaction with the Z3 SMT solver. Under the hypotheses of Theorem \ref{Th:finiteness}
-this algorithm terminates.
+semantics, its new ``on-the-fly'' version, and the interaction with the
+Z3 SMT solver. Under the hypotheses of Theorem \ref{Th:finiteness} 
+both algorithms terminate.
 
@@
 the predicate of each OT is translated 
-into SMTlib assertions, and checked for satisfiability (function \texttt{filterUnsatTransitions}).
+into SMTlib assertions (see Section~\ref{section:pruning}), and checked for
+satisfiability (function \texttt{filterUnsatTransitions}).\\ 
 Then we compute the set of reachable transitions and states to build
@@
 When applying a rule to a PLTS at the leaves, we simply take the PLTS transitions of the
-corresponding local state and use the semantic rule to build the OT\footnote{%
-	%
-	We omit detailed presentation of this case for the sake of brevity.
-	%
-}.
+corresponding local state and use the semantic rule to build the OT.
 When applying a rule to a pNet node we use two methods, combining and
@@
 holes of the node, so \emph{MakeTransitions} is never called on a hole.
-
-%
-%% \noteInSB{Algorithm~\ref{alg2}, as presented below is not
-%%   well-defined: when we reach the leaves, a pLTS does not have any
-%%   subnets, hence the loop in lines 2--4 is empty and so is the list
-%%   $l$. $\mathit{Combining}(l)$ is then called on an empty list...}
-
-%\noteInSB{Line 2: Tr1 and Tr2 are the semantic rules, right?}
-
-%% \noteInSB{Line 6: Nothing in the assignment $\overline{comb} =
-%%   \mathit{Combining}(l)$ depends on $sv$.  Hence, this should probably
-%%   be done outside of the loop.}
-
-%% \noteSB{Line 7: There are two type mismatches here: $ot$ is an open
-%%   transition, whereas $\mathit{Matching}$ is a predicate\mdash one
-%%   cannot assign a predicate to an open transition.  Furthermore, in
-%%   the definition of $\mathit{Matching}$, below, $C_n$ is an open
-%%   transition, whereas $\overline{comb}$ is a {\em set} of open
-%%   transitions, so this call does not type either. There is probably
-%%   another inner loop over all tuples of OTs in $\overline{comb}$; even
-%%   so the open transition has to be defined completely, not just the
-%%   predicate\mdash what is the value of $Post$ for the new transition?
-%%   Maybe $\mathit{Matching}$ should not be a predicate, but an OT?
-%%   Finally, how is $\mathit{hole}$? (I have removed $v$\mdash here and
-%%   in the parameters of the definition of the $\mathit{Matching}$
-%%   predicate, because the text in the paragraph ``Matching'' says that
-%%   $v$ is fresh.)}
-%% \noteEM{Done, please check the new version}
-
-%\noteInSB{Line 8: When is $\mathit{Filter}(ot)$ called?}
 
@@
 \label{section:use-cases}
-\TODO{new section here, showing various features on different examples}
-
-\subsection{Enable Operator} in Lotos, with (equivalent) state-based
-and data-based encodings; Associativity of Enable;
+In this section we present the results of open automata construction
+for several examples, starting with three constructions from
+Section~\ref{section:running-example} using the Enable operator.
+Then we give detailed results for the Failure Controller that was
+presented in \cite{AVOCS18}, and show how this sort of BIP Architectures
+can be composed together.
+Finaly we give some figures illustrating the benefits from the smart
+algorithm on these examples.
+
+\subsection{Enable operator} 
 \label{section:use-case:Enable}
 
-\begin{figure}[~tb]
+\begin{figure}[ht]
 \centerline{ 
@@
 
-The open automata generated for the 2 encodings of Enable in
+The open automata generated for the two encodings of Enable in
 Figure~\ref{schema:enable-pnets} are displayed in
-Figure~\ref{schema:enable-OAs}. We have shown in \ref{Forte} how to
+Figure~\ref{schema:enable-OAs}. We have shown in \cite{henrio:Forte2016} how to
 prove that these two automata are bismilar.
 
-Now 
 %%\subsection{simple communication protocol} specification and implementation;
@@
 \subsection{BIP FailureTimer Architecture}
-\label{section:FailureTimerMax}
+\label{section:FailureTimer}
 
@@
 \subsection{Composing Two FailureTimer BIP Architectures}
-\noteInEM{Modifications stopped here}
 \label{section:use-case:Double}
-\TODO{Enhanced FailureTimer, 2 instances composed, with duplicated control and Timer}
-
-In the conception of the nanosatellite software \cite[], the FailureTimer architecture was used to control several processes
+
+In the conception of the nanosatellite software \cite{CubETH-case-study}, the FailureTimer architecture was used to control several processes
 communicating on the common bus. Timeout signals (``$ask$''), resets,
@@
 
-In each cell of the following table, we display the number of OTs whose predicates were founSAT/UNSAT by the SMT engine, and the overall time spent for the execution of the whole algorithm.
+In each cell of the following table, we display the number of OTs whose predicates were found SAT/UNSAT by the SMT engine, and the overall time spent for the execution of the whole algorithm.
+
+All tests are run on HP xxx laptop under Windows 10 x64, with a Intel quad-Core i7-6600U
+processor, and 32Gb of RAM. The software platform is VerCors\footnote{Available at \url{https://team.inria.fr/scale/software/vercors/}.}, running on top of
+Eclipse Equinox, with Java 1.8.
 
@@
 
-        This shows a significant benefit of the ``smart'' strategy, in the considered use-cases, between 30\% and 80\% gain depending on the examples.
+        \medskip
+        In the basic cases (EnableState, EnableData) there is no
+        benefit, and even an overhead in the case of EnableData,
+        because of the extra step of checking SAT at the end of the
+        algorithm.
+But as soon as there are more OTs in the system and not all
+states are reachable, these tests show a significant benefit of the ``smart'' strategy, in
+the considered use-cases, with 50\% of time saving for the FailureTimer,
+over to 80\% for the composition, depending
+        on the nature of the examples, but increasing significantly
+        with their complexity.
 
@@
 for analysing our symbolic transitions will not make the approach too expensive
-in terms of computing time. In~\cite{Avocs-RR}, we show that, for a slighly bigger example of assembling two failure controllers, Z3 can check the
+in terms of computing time. We tried a
+slightly bigger example, assembling two Failure
+controllers. In~\cite{Avocs-RR}, we show that Z3 can check the 
 satisfiablility of a 90K open transitions in a couple of minutes.

### 2019-03-24 2017-Xudong-SMT/ActaInformatica.tex
several minor changes

@@
 \ERIC{We also propose and implement an optimised
-	algorithm that performs part of the pruning on-the-fly, and show how
+	algorithm that performs part of the pruning on-the-fly, and show 
 	this new algorithm is correct with respect to the original one.
@@
 	classical process-algebra operator for which we provide several
-	encodings, and prove basic properties. The second is  industry-oriented and based on the so-called ``BIP architectures'', which have
+	encodings, and prove some basic properties. The second is  industry-oriented and based on the so-called ``BIP architectures'', which have
 	been used to specify the
@@
 method for these processes. 
-Later on, symbolic semantics were extended to the $\pi$-calculus \cite{Milner99} and decision algorithms for various symbolic bisimulations were proposed \cite{Li99,Deng2001}. However, no
+Later on, symbolic semantics was extended to the $\pi$-calculus \cite{Milner99} and decision algorithms for various symbolic bisimulations were proposed \cite{Li99,Deng2001}. However, no
 practical verification platform has been developed to use this kind of approaches to provide proof methods for
@@
 Traditionally, pNets have been used to formalise fully
-defined systems or softwares. But we want also to define and reason
+defined systems or softwares. But we  also want to define and reason
 about incompletely defined systems, like program skeletons, operators,
@@
 The open pNet model addresses this problem, using
-``holes'' as process parameters, representing \emph{unspecified} subsystems.
-The pNet model was developed in a series of
+\emph{holes} as process parameters, representing \emph{unspecified} subsystems.
+The open pNet model was developed in a series of
 papers~\cite{HMZ:PDP15,henrio:Forte2016} in which many examples have been
@@
 open systems encoded as pNets. The equivalence between pNets is
-``FH-bisimulation'' \cite{henrio:Forte2016}, a dedicated version of
-symbolic bisimulation taking the  
-predicate of the open transitions into account when matching such
+FH-bisimulation \cite{henrio:Forte2016}, a dedicated version of
+symbolic bisimulation taking 
+predicates into account when matching 
 open transitions. We foresee that the interplay with the SMT solver
-that we use here for satisfiability of open transitions will be
+that we use here for satisfiability of the predicates of open transitions will be
 similar to what we need when proving (symbolic) equivalence between open
-transitions.
+pNets.
 
@@
 	VerCors platform. In the process, we improve the
-	semantics rules from~\cite{henrio:Forte2016}, and add features in
+	semantic rules from~\cite{henrio:Forte2016}, and add features in
 	the algorithm to deal with the full 
@@
 In Section \ref{section:implementation} we present an algorithm to compute this semantics, including the interaction with Z3.
-In Section~\ref{sec:cases} we give a few use-cases, in particular, a BIP
+In Section~\ref{section:use-cases} we give a few use-cases, in particular, a BIP
 architecture from the nano-satellite case-study. 
@@
 family is written $\emptyset$. We
-denote classically $\overline{a}$ a family when the indexing set is
+denote by $\overline{a}$ a family when the indexing set is
 irrelevant. The symbol $\uplus$ stands for the disjoint union of indexed sets.
@@
 The definition of an algebra presentation and a set of variables
-$\P$ fix the term algebra elements $\Talg, \AlgB_{\P}, \AlgA_\P$.
+$\P$ fix the term algebra elements $\Talg, \AlgB_{\P},$ and $\AlgA_\P$.
 
@@
 %suppose that transitions looping to the same state does not do assignments.
-Note that we make no assumptions on finiteness of the set of states, nor
+Note that we make no assumption on finiteness of the set of states, nor
 on finite branching of the transition relation.
@@
 We first define the set of actions a PLTS can use.  Let $a$
-range over action labels, $\symb{op}$ are operators, and $x_i$ range over
-variable names. Action terms are:
+range over action labels, $\symb{op}$ over operators, and $x_i$  over
+variable names. Action terms are given by the following grammar:
 \[
@@
 In Figures~\ref{schema:enable-pnets},\ref{schema:enable-composed}, we show
-examples of these constructs, with two pLTSs, one hole and one pNet
+examples of these constructs, with two PLTSs, one hole and one pNet
 node encoding our running example.
@@
 %  assignments}
-LTSs with the actions of some holes; the transition occurs if some predicates hold,
+LTSs with the actions of some holes; a transition occurs if its predicates hold,
 and can involve a set of state modifications. Each state of an open
@@
 	\begin{itemize}
-		\item[$\bullet$]  $I$ and $J$ are  sets of indices,
+		\item[$\bullet$]  $I$ and $J$ are  two sets of indices,
 		%	\item[$\bullet$]  $LTS_i^{i\in I}$ is a family of LTSs,
@@
 in structured states as $\triangleleft\ldots\triangleright$).
-For any pNet p, let $\overline{\mathit{Leaves}} = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be the set of PLTSs at its leaves,
+For any pNet $p$, let $\overline{\mathit{Leaves}} = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be the set of PLTSs at its leaves,
 then $\mathit{States}(p) = \{\ostate{s_i^{i\in L}}
@@
 
-\paragraph{Structural Semantic Rules:}
+\paragraph{Structural Semantic Rules.}
 The semantics of pNets in terms of open automata has been defined in
@@
 
-In \cite{henrio:Forte2016} we also proved the following result, that
-ensure that the termination of our semantic construction algorithm:
+In \cite{henrio:Forte2016} we also proved the following result, which
+ensures the termination of our semantic construction algorithm.
 \begin{theorem}[Finiteness]
@@
 into SMTlib assertions (see Section~\ref{section:pruning}), and checked for
-satisfiability (function \texttt{filterUnsatTransitions}).\\ 
+satisfiability (function \texttt{filterUnsatTransitions}). 
 Then we compute the set of reachable transitions and states to build
@@
 is the disjoint union
-of sets of state variables of the individual PLTS states constituting this
+of the sets of state variables of the individual PLTS states constituting this
 global state. \ERIC{The final assignment sets are assembled when building the
@@
 variables of such state, so narrowing it means we get a better
-approximation, and potentialy more information, that can be used to
+approximation, and potentially more information, which can be used in
 the SAT checking of subsequent transitions. But we \emph{cannot} use this
@@
 they cannot be complete before exploring (at least) all the reachable
-state space. So the smart algorithm performs in two steps: during the
+state space. So the smart algorithm proceeds in two steps: during the
 first step, the SAT checking is done without using any assignment set
@@
 making the behaviour depending on the value of input variables. But
-the open automaton need not to collect the set of possible values dealing
+the open automaton needs not to collect the set of possible values dealing
 with the values of local variables, so we can directly compute the
@@
 algorithm, without final reachability computation, computes exactly
-the same open automaton as Algorithm 1.
+the same open automaton as that of Algorithm 1.
   \end{theorem}
@@
 
-\begin{theorem}[Correctness without assignments]
+\begin{theorem}[Correctness with assignments]
   \label{Th:CorrectnessWithAssignments}
@@
 algorithm, with a final reachability computation, computes exactly
-the same open automaton as Algorithm 1.
+the same open automaton as that of Algorithm 1.
 \end{theorem}
@@
 Z3 using its Java API. Here, for readability, we
-show the Z3 code using its SMT-LIB input language.
+show the Z3 code using its SMTlib input language.
 Note that in the previous sections, the OTs were displayed in a
@@
 SMTlib declarations (\texttt{declare-datatypes} and
-\texttt{declare-fun}). We also formalise a condition of well-formedness of pNets to ensure that the generated code is correct,
+\texttt{declare-fun}). We also formalise a condition of well-formedness of pNets to ensure that the generated code is correct
 and will not raise runtime errors in the SMT engine. Note that the
@@
 names from our example.
-Additionally, we will include axiomatisation of any required functions
+In addition, we will include axiomatisation of any required functions
 and predicates of the presentation data-types.
@@
 Figure~\ref{schema:enable-OAs}. We have shown in \cite{henrio:Forte2016} how to
-prove that these two automata are bismilar.
+prove that these two automata are bisimilar.
 
@@
 reset, unless a resumption is registered within $\mathrm{Max}$ time
-units (more details in Sect.~\ref{section:FailureTimer}).
+units (more details in Secion.~\ref{section:FailureTimer}).
 
@@
 be synchronous: each can only tick after the other has also started,
-and then they will tick, and timeout, synchrounously.
+and then they will tick, and timeout, synchronously.
 
@@
 
-All tests are run on HP xxx laptop under Windows 10 x64, with a Intel quad-Core i7-6600U
+All tests are run on HP xxx laptop under Windows 10 x64, with an Intel quad-Core i7-6600U
 processor, and 32Gb of RAM. The software platform is VerCors\footnote{Available at \url{https://team.inria.fr/scale/software/vercors/}.}, running on top of
@@
 definitely be useful when comparing different pNets with
-different structure. For bisimulation, we foresee that SMT methods
+different structures. For bisimulation, we foresee that SMT methods
 will be the basis for comparing open transitions. 
@@
 controllers. In~\cite{Avocs-RR}, we show that Z3 can check the 
-satisfiablility of a 90K open transitions in a couple of minutes.
+satisfiablility of  90K open transitions in a couple of minutes.
 

### 2019-03-24 2017-Xudong-SMT/ActaInformatica.tex
Draft proof of Th.2 and Th.3.

@@
 
+\begin{proof}
+
+Intuitively, $\forall \ostate{\tilde{s}}\in\textit{Explored}=State(L)\text{, there must exist a transition}\ostate{\tilde{s_i}}\xrightarrow{v_i}\ostate{\tilde{s}}\text{ and }\forall \ostate{\tilde{s}}\in\textit{Explored}_{Smart}=State(L_{Smart})\text{, }\exists\ostate{\tilde{pre(s)}}\text{, }\ostate{\tilde{pre(s)}}\xrightarrow{v}\ostate{\tilde{s}}\text{ where \textit{Pred} is satisfiable and the state}\ostate{\tilde{pre(s)}}\text{ has two cases:}$
+\begin{enumerate}
+	\item[(1)] $\ostate{\tilde{pre(s)}}=\ostate{\tilde{s}}$
+	\item[(2)] $\ostate{\tilde{pre(s)}}\in\textit{Explored}\text{-}\{\ostate{\tilde{s}}\}$
+\end{enumerate}
+By induction, there must exists a sequence $\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s}}$ where all the $\textit{Pred}_i$ are satisfiable.
+
+Then $\forall\ostate{\tilde{t}}\textit{Explored}=State(L)$, there are also two cases:
+\begin{enumerate}
+	\item[(1)] $\ostate{\tilde{t}}\in State(L1)$
+
+	By definition of reachability, there exists a sequence $\ostate{\tilde{s_0}}...\xrightarrow{v_j}...\ostate{\tilde{t}}$ where all the $\textit{Pred}_j$ are satisfiable.
+
+	$\Rightarrow \ostate{\tilde{t}}\in State(L_{Smart})$
+	\item[(2)] $\ostate{\tilde{t}}\in State(L)\text{-}State(L1)$, then $\forall \ostate{\tilde{u}}\in\textit{Explored}-\{\ostate{\tilde{t}}\}$,
+	\begin{enumerate}
+		\item[(1)] $\ostate{\tilde{u}}\in State(L)\text{-}State(L1)$.
+		\item[(2)] $\ostate{\tilde{u}}\in State(L1)$, but there is no transition $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{t}}$.
+		\item[(3)] $\ostate{\tilde{u}}\in State(L1)$, there exists transition $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{t}}$, but the $\textit{Pred}_u$ is unsatisfiable.
+	\end{enumerate}
+	By induction, there is no sequence from $\ostate{\tilde{s_0}}$ to $\ostate{\tilde{t}}$.
+
+	$\Rightarrow \ostate{\tilde{t}}\notin State(L_{Smart})$
+\end{enumerate}
+Overall, $State(L1)$ is equal to $State(L_{Smart})$.
+\end{proof}
+
 But in the presence of assignments, we need to collect all of them
@@
 \TODO{Xudong: proof}
+
+\begin{proof}
+In Theorem 2, we have already proved the result set of global states of two algorithm are the same without the assignments.
+
+If there exists assignments in the open transitions.
+
+In Algorithm 3, $\forall\ostate{\tilde{t}}\notin State(L_{Smart})$, if there is a transition $\ostate{\tilde{t}}\xrightarrow{v_t}\ostate{\tilde{t'}}$ contains an assignment $\textit{Post}_t$, and in following transitions $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{u'}}$, we need to check $\textit{Pred}\and\bigwedge\textit{Post}_i$ where $\textit{Post}_i \notin \{\textit{Post}_t\}$.
+
+In Algorithm 1, the same state $\ostate{\tilde{t}}\notin State(L1)$, also has a transition $\ostate{\tilde{t}}\xrightarrow{v_t}\ostate{\tilde{t'}}$ contains an assignment $\textit{Post}_t$, and in following transitions $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{u'}}$, what need to check is $\textit{Pred}\and\bigwedge\textit{Post}_i$.
+As $b_1\and b_2\rightarrow b_1$, if $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{u'}}$ exists in the result of Algorithm 3, it is also contained in the original result.
+
+After the final reachability computation, $\{\textit{Post}_t\}$ is removed from $\{\textit{Post}_i\}$ then the assertions to check become the same, then the transitions of the result are also the same.
+So the result open automaton of Algorithm 3 is exactly the same as that of  Algorithm 1.
+\end{proof}
 
@@
 \centerline{ 
-  \includegraphics[width=0.30\linewidth]{ActaXFIG/Enable1-aut}
+  \includegraphics[width=0.30\linewidth]{ActaXFIG/Enable1}
   \hspace{25mm}
-  \includegraphics[width=0.25\linewidth]{ActaXFIG/Enable2-aut}}
+  \includegraphics[width=0.25\linewidth]{ActaXFIG/Enable2}}
   \begin{minipage}{5.7cm}

### 2019-03-25 2017-Xudong-SMT/ActaInformatica.tex
update figures, figure comments, and todos

@@
 
-\TODO{Add new contrib}
-\todoMargin{Should we remove Min ?}
-\keywords{pNets, software components, symbolic semantics, SMT
+%% \TODO{Add new contrib}
+%% \todoMargin{Should we remove Min ?}
+\keywords{Networks of synchronised automata, software components, symbolic semantics, SMT
 	%Networks of Synchronised Automata, Symbolic Behavioral Semantics, Compositional Analysis of Software Components, SMT}
@@
 		\\\hline\specialrule{0em}{1pt}{1pt}
-		\multicolumn{3}{l}{\sl Extension for the BIP use-case of Figure~\ref{schema:ArchFailure:pNet}}
+		\multicolumn{3}{l}{\sl Extension for the Enable use-case of Section~\ref{section:running-example}}
 		\\\hline\specialrule{0em}{1pt}{1pt}
-		Action & \multicolumn{2}{l} \texttt{FUN\_Action\_Bool}, \texttt{}fail, resume, timeout, reset, start, tick, ask 
+		Action & \texttt{ACT}, \texttt{delta, acc}  &
 		\\\hline
@@
 \cite{henrio:Forte2016}, in the form of two structural rules, one for
-PLTSs, and the other for pNet nodes. These rules are slightly improved, adding guards in the synchronisation vectors and syntax for universal quantifier in the guards (see~\cite{Avocs-RR}).
+PLTSs, and the other for pNet nodes.
+These rules are slightly improved, adding guards in the synchronisation vectors and syntax for universal quantifier in the guards (see~\cite{Avocs-RR})\footnote{For convenience, we provide these rules and the proof of the finiteness theorem in Appendix~\ref{appendix:semRules}}.
 
@@
   Remark that all the elements of such pNets and open automata are symbolic, and they can represent many classes of unbounded systems.
-
-\begin{proof}
-  \TODO{I tentatively copied the proof here, from RR-8898.
-the proof of the finiteness theorem refers to SOS rules Tr1 and
-  Tr2. Yuxin, I agree this proof is NOT required in this paper. But for the
-  sake of reviewing process, (and if I find enough time), I will try
-  to add an appendix with the semantic rules (Tr1 and Tr2, constructing open
-  transitions from pNets) and the proof of finiteness below }
-
-  The possible set of states of the open-automaton is the cartesian
-  product of the states of the pNet $pLTS_i^{i\in L}$, that is finite by
-  hypothesis. So the top-level residual loop of Algorithm 1 terminates provided each 
-  iteration terminates. The enumeration of open-transitions in step 2b is bounded by the
-  number of applications of rules Tr2 on the structure of the
-  pNet tree, with a finite number of synchronisation vectors applying
-  at each node the number of global open transitions is finite. Similarily rule Tr1 is 
-  applied finitely if the number
-  of transitions of each pLTS is finite. So we get finitely many deduction trees, and
-  open-transitions which ensures that each internal loop of Algorithm 1 terminates.
-  \end{proof}
 
@@
 unsatisfiable open transition 
-from the open automaton of our running example. \TODO{change the text}It shows the case where
-the failure controller performs a ``$\PortFail$'' action, while the timer
-executes a ``$\PortResume$''. The chosen synchronisation
-vector (SV0 from Figure~\ref{schema:ArchFailure:pNet}) does not match
-with these actions, since it expects $\NameTimer.\PortStart$. This
+from the open automaton of our running example.
+
+It shows the case where processes $P$ and $R$ ``try'' to communicate directly, $P$, but this is made impossible by the combination of chosen synchronisation vectors and their guards. This
   mismatch is materialised by the predicate
-fragment ``$\mathit{resume}(\false)=\mathit{start}(b_2)$''.
+fragment ``$a1 = \delta(x2) \land \forall z. a1 \neq \delta(z)$''. In Section~\ref{section:TranslationToSMTlib} we will show how this is encoded and checked using the SMT engine.
 
@@
           \inferrule*[myfraction=\reddottedrule]
-	{\{\xrightarrow{\delta(x2)}_P ~~
+	{\{\xrightarrow{a1}_P ~~
           \xrightarrow{acc(x2)}_R \} ~~
-          [\forall z. \delta(x2) \neq \delta(z) \neq
-            \delta(x2)]
+          [a1 = \delta(x2) \land \forall z. a1 \neq \delta(z)]
         }
@@
 	\end{mathpar}
-\caption{\TODO{Eric: check, it looks wrong}One of the unsatisfiable open transitions}  \label{schema:unsat-ot}
+\caption{One of the unsatisfiable open transitions}  \label{schema:unsat-ot}
 \end{figure}
@@
 symbolic automaton is still logically correct.
-
-\TODO{Yuxin: I can add an example showing in detail why we cannot use
-  the assignment information on the fly. Do you think this is useful,
-  or id the explanation above sufficient ?}
-{\color{green} Yuxin: I think the explanation above is sufficient. What's more important is to give formal proofs for the three theorems.}
 
@@
 
-\TODO{Xudong: proof}
+\TODO{Need to refine theorem, and to check the proof... To answer
+  Yuxin question about ``exactly the same'', indeed it is not
+  correct... But not for states: state labels will be exactly the
+  same. But transitions will not, because of the mechanism for
+  generating fresh variables; so we may need to reword as ``bijective''}
 
@@
 
-\TODO{Xudong: proof}
+\TODO{Xudong: proof - to be checked}
 
@@
 
-\TODO{Eric : Eventually provide counter-example for smart with unsing incomplete
-  assignment sets}
-
 \subsection{Translation to SMTlib}
+\label{section:TranslationToSMTlib}
 
@@
 in the SMTlib syntax.
-\TODO{Change the text}It contains the declaration
-of the BIP action algebra sorts 
+\TODO{Change the text: DONE}It contains the declaration
+of the relevent part of the Lotos action algebra sorts 
 and constructors, then the declaration of variables, and finally the
 predicate to be checked, encoded as a set of assertions.
-Here the behavior of the hole ``B'' appears as a variable
-``|hb\_B:13:1|'', and line 10 shows the constraint that matching with
-a synchronisation vector has imposed on the behavior of ``B''.
+
+Here the behavior of the hole ``P'' ($a1$ in Figure~\ref{schema:unsat-ot}) , after matching with the synchronisation vectors, appears as a variable
+``|a1:sva\_SVA0:15:1|'', and ``R'' ($acc(x2)$) as ``|(ACT delta
+|x:sva\_SV4:1:2|''. Line 16 requires that $a1 = \delta(x2)$ to match
+the second synchronisation vector of the root pNet node, and lines
+17-18 that $a1$ does not match $\delta(x1)$ for any $x1$. 
 We also display  the diagnosis (``sat'' or ``unsat'') generated by Z3.
@@
 
-For simplicity, we have only shown here a use-case with boolean data
-parameters, so we only require the basic SAT capability of the Z3
+For simplicity, we have only shown here a use-case with boolean conditions, so we only require the basic SAT capability of the Z3
 engine. It should be clear that more involved examples will require
@@
 %%\subsection{simple communication protocol} specification and implementation;
+\TODO{Eric: more results: enable associativity}
 
@@
 \label{section:FailureTimer}
+
+\TODO{Simon: reduce...}
 
@@
 and then they will tick, and timeout, synchronously.
+
+\TODO{Eric: try reorganise the figures. Add properties ?}
 
@@
 
+\TODO{add the novelties...}
+
 %% Among the questions that have arised during this work, an important one is the
@@
 \bibliographystyle{spmpsci}
-
-% \bibliography{oasis,biblio}
 \bibliography{biblio}
 
-\end{document}
-
-%\newpage
 \appendix
-\section{Changes from pre-proceedings version}
-All minor requests from reviewers (typo, grammar) were already corrected in the preproceedings version.
-
-Request from Reviewer 3, that we had not done in the preproceedings, for matter of space, have now been shortly answered.
-More precisely,
-\begin{itemize}
-\item{} in section \ref{section:op-semantics}, we have added a precise statement of our finiteness theorem, that answers the question about termination of the algorithm.
-\item{-} in section \ref{section:pruning} we have added more explanations about the way that various data types theories will be handled by the SMT engine
-\end{itemize}
-
-The following appendices are included for the convenience of reviewers.
-Our intention is to publish as a research report, before final publication, an
-extended version containing all technical details, proofs, and more examples.
-
-The appendices are organized in the following way:
-
-\begin{enumerate}
-\item[A] pNet semantic rules
-\item[B] Variable management
-  \subitem B.1 fresh variables
-  \subitem B.2 managment of state variables
-\item[C] Algebra presentations
-\item[D] Well-formness and typing of expressions
-\item[E] Translation to SMTlib input language
-\item[F] Full output for the FailureTimer open automaton
-\item[G] Scaling up
-
-\end{enumerate}
 
@@
 the previous section. 
-%given by Definition~\ref{def-states}.
 To build an open transition one first
@@
 pLTS transitions on these states, and compose them with actions of
-holes using synchronisation vectors. %The pNet
-%structure does not appear in the open-automaton, only the
-%set of Holes and the set of Leaves.
+holes using synchronisation vectors.
 
@@
 application of Tr2 have to be fresh and all distinct.
-
-% The semantic of the open pNets is already defined as an open automaton
-% in \cite{henrio:Forte2016} using open transitions to present the
-% transitions of its global states.
 
@@
   \end{description}
-% Note that this note is greatly simplified by the fact that variables are local to 
-% thread; introducing global state variables or accepting loops to the same 
-% state would 
-% require to reason 
-% on the scope of 
-% each variables, and to introduce additional variables to handle the several occurence 
-% of the same pLTS variable in the predicates. Indeed the constraints on pLTS 
-% transitions 
-% ensure that the same variable never appears both on the left and on the right of the 
-% equations of a predicate.
 
@@
   Leaves, $L_k$ the index set of the leaves of one subnet, so all $L_k$
-  are disjoint subsets of $L$. % Thus the states in the open transitions,
-%   at each level, are tuples including states of all the
-%   leaves of the pNet, not only those involved in the chosen
-%  synchronization vector.
+  are disjoint subsets of $L$.
 
@@
 \begin{theorem}[Finiteness of open-automata.]\\
+Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $pLTS_i^{i\in I}$ and holes $Hole_j^{j\in
+  J}$, if the sets $I$ and $J$ are finite, if the synchronization vectors of all pNets 
+  included in  $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ 
+  are finite, and if
+$\forall i \in I.\, finite{(states(pLTS_i))} \text{ and } pLTS_i$
+has a finite number of state variables, then Algorithm 1 terminates
+and produces an open automaton 
+$\mathcal{T}$ with finitely many states and transitions.
+
+\end{theorem}
+
+\begin{proof}
+  The possible set of states of the open-automaton is the cartesian
+  product of the states of the pNet $pLTS_i^{i\in I}$, that is finite by
+  hypothesis. So the top-level residual loop of Algorithm 1 terminates provided each 
+  iteration terminates. The enumeration of open-transitions in step 2b is bounded by the
+  number of applications of rules Tr2 on the structure of the
+  pNet tree, with a finite number of synchronisation vectors applying
+  at each node the number of global open transitions is finite. Similarily rule Tr1 is 
+  applied finitely if the number
+  of transitions of each pLTS is finite. So we get finitely many deduction trees, and
+  open-transitions which ensures that each internal loop of Algorithm 1 terminates.
+  \end{proof}
+
+\end{document}
+
+%\newpage
+\appendix
+\section{Changes from pre-proceedings version}
+All minor requests from reviewers (typo, grammar) were already corrected in the preproceedings version.
+
+Request from Reviewer 3, that we had not done in the preproceedings, for matter of space, have now been shortly answered.
+More precisely,
+\begin{itemize}
+\item{} in section \ref{section:op-semantics}, we have added a precise statement of our finiteness theorem, that answers the question about termination of the algorithm.
+\item{-} in section \ref{section:pruning} we have added more explanations about the way that various data types theories will be handled by the SMT engine
+\end{itemize}
+
+The following appendices are included for the convenience of reviewers.
+Our intention is to publish as a research report, before final publication, an
+extended version containing all technical details, proofs, and more examples.
+
+The appendices are organized in the following way:
+
+\begin{enumerate}
+\item[A] pNet semantic rules
+\item[B] Variable management
+  \subitem B.1 fresh variables
+  \subitem B.2 managment of state variables
+\item[C] Algebra presentations
+\item[D] Well-formness and typing of expressions
+\item[E] Translation to SMTlib input language
+\item[F] Full output for the FailureTimer open automaton
+\item[G] Scaling up
+
+\end{enumerate}
+
+\section{pNet semantic rules}
+\label{appendix:semRules}
+
+\paragraph{Note:} For convenience, we have included here the semantic rules for pNets,
+that were already published in \cite{henrio:Forte2016}.
+
+We build the semantics of an open pNet as an open automaton where
+LTSs are the pLTSs at 
+the pNet leaves, and the states are structured as in
+the previous section. 
+%given by Definition~\ref{def-states}.
+To build an open transition one first
+ projects the global state into states of the leaves, then applies
+pLTS transitions on these states, and compose them with actions of
+holes using synchronisation vectors. %The pNet
+%structure does not appear in the open-automaton, only the
+%set of Holes and the set of Leaves.
+
+The semantics   regularly instantiates \emph{fresh} variables, and uses a
+\emph{clone} operator that clones a term replacing each variable with a
+fresh one.
+The variables in each synchronization vector are considered local:
+for a given pNet expression, we must have fresh local variables for
+each occurrence of a vector (= each time we instantiate rule
+Tr2). Similarly the state variables of each copy of a
+given pLTS in the system, must be distinct, and those created for each
+application of Tr2 have to be fresh and all distinct.
+
+% The semantic of the open pNets is already defined as an open automaton
+% in \cite{henrio:Forte2016} using open transitions to present the
+% transitions of its global states.
+
+\begin{definition}[Operational semantics of open pNets]
+  \label{def:operationalSemantics}
+  The semantics of a pNet $p$ is an open automaton $A = <Leaves(p),J,\mathcal{S}, s_0,
+  \mathcal{T}>$ where:
+  \begin{itemize}
+    \item $J$ is the indices of the holes: $Holes(p)= H_j^{j\in J}$.
+    %  \item $\overline{L}^L = Leaves(p), \overline{H}^J = Holes(p)$
+    \item $\overline{\mathcal{S}} = States(p)$ and $s_0 = InitState(p)$
+    \item $\mathcal{T}$ is the smallest set of open transitions
+    satisfying the rules below:
+  \end{itemize}
+
+  The rule ({\bf Tr1}) for a pLTS $p$  checks that the guard 
+  is verified and transforms assignments into post-conditions:
+
+  \begin{description}
+    \item[{\bf Tr1:}]
+    $\inferrule
+    { s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
+          J}\rangle} s'\in \to  \\
+      {\tt fresh}(v) \\
+      Pred = ~e_b \land (v = \alpha)
+    }
+    { p = \mylangle  S,s_0, \to \myrangle
+      \models
+      \inferrule*[myfraction=\reddottedrule]
+      {\{s \xrightarrow{\alpha}_p s'\} ,\emptyset ,
+      Pred,\left\{x_j\gets e_j\right\}^{j\in J}}
+      {\ostate{s} \xrightarrow{v} \ostate{s'}}
+    }
+    $
+  \end{description}
+% Note that this note is greatly simplified by the fact that variables are local to 
+% thread; introducing global state variables or accepting loops to the same 
+% state would 
+% require to reason 
+% on the scope of 
+% each variables, and to introduce additional variables to handle the several occurence 
+% of the same pLTS variable in the predicates. Indeed the constraints on pLTS 
+% transitions 
+% ensure that the same variable never appears both on the left and on the right of the 
+% equations of a predicate.
+
+  The second rule ({\bf Tr2}) deals with pNet nodes: for each possible
+  synchronization vector applicable to the rule subject, the premisses
+  include one {\em open transition} for each sub-pNet involved, one possible
+  {\em action} for each Hole involved, and the predicate relating these
+  with the resulting action of the vector.
+  A key to understand this rule is that the open transitions are
+  expressed in terms of the leaves and holes of the pNet structure,
+  i.e. a flatten view of the pNet: e.g. $L$ is the index set of the
+  Leaves, $L_k$ the index set of the leaves of one subnet, so all $L_k$
+  are disjoint subsets of $L$. % Thus the states in the open transitions,
+%   at each level, are tuples including states of all the
+%   leaves of the pNet, not only those involved in the chosen
+%  synchronization vector.
+
+  \begin{description}
+    \item[{\bf Tr2:}]
+  \end{description}
+
+  \noindent
+    $\inferrule
+    {k\!\in\! K \\ SV\!\!= \!clone(SV_k) \!=\! \alpha_m^{m \in I_k\uplus J_k} \!\to\! 
+    \alpha'_k, G_k \\
+      Leaves(p) \!=\! \pLTS_l^{l\in L} \\     
+      \forall m\in I_k.
+      \pNet_m \models
+      \inferrule*[myfraction=\reddottedrule]
+      {\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
+      \{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
+      {\ostate{s_{i}^{i \in L_m}} \xrightarrow {v_m}
+        \ostate{s_{i}^{\prime\ i \in L_m}}}
+      %\land
+      %Leaves(\pNet_m) = \overline{pLTS}^{L_k})
+      \\
+      I' = \biguplus_{m\in I_k}\!\! I_m'
+      \\ J' = \biguplus_{m\in I_k}\!\! J'_m \uplus J_k  \\
+      \Pred = \bigwedge_{m\in I_k}\!\! \Pred_m \land
+      \MkPred(SV,v_m^{m\in I_k},b_j^{j\in J_k},v)\\
+      \forall j\!\!\in\!\! J_k. {\tt 
+        fresh}(b_j) \\ {\tt fresh}(v) \\ 
+      \forall i\in
+      L\backslash I'.\,s'_i=s_i 
+    }
+    {p = \mylangle \pNet_i^{i\in I}, S_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle
+      \models
+      {\inferrule*[myfraction=\reddottedrule]
+        {\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I^\prime},
+        \{\xrightarrow{b_j}_j\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_k} 
+        \Post_m}
+        {\ostate{s_i^{i\in L}} \xrightarrow {v}
+          \ostate{s_i^{\prime i\in L}}}
+      }
+    }
+    $
+
+  \medskip  
+\end{definition}
+
+In rule TR2, the generated predicate is composed of the conjunction of
+the predicates of the subnets' OTs, with the additional part encoding
+the application of the chosen synchronisation vector.
+In \cite{henrio:Forte2016} this last part is defined as:
+\[\MkPred(SV_k, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow
+\begin{array}{l}
+\exists {(a'_i)}^{i\in I},
+{(b'_j)}^{j\in J},v'.\, SV_k={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v'
+\\~~\land
+\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v'
+\end{array}\]
+
+%% This definition is not constructive, but the existentialy quantified
+%% variable sets here correspond the subsets of subnets and holes that
+%% are effectively involved in vector $SV_k$.
+%% Within our algorithm, these subsets have been computed by $Combining$ and
+%% passed as arguments to the $Matching$ method, so
+%% we can construct this predicate fragment as:
+
+%% \[\Pred(SV, \overline{\pNet},\overline{S}, v) = 
+%% \begin{array}{l}
+%% \forall {(a'_i)}^{i\in I},
+%% {(b'_j)}^{j\in J},v'.
+%% \\
+%% v_m=a'_i\land \, b_j=b'_j \land v=v' \land G_k
+%% \end{array}\]
+%% \TODO{Eric: to be checked}
+
+Within our algorithm, these subsets have been computed by the
+$Combining$ method and passed as arguments to the $Matching$ method
+(see section~\ref{section:implementation})
+
+\paragraph{Termination.} To have some practical interest, it is important to know when this
+algorithm terminates. The following theorem shows that an open-pNet
+with finite synchronization sets, finitely many leaves and
+holes, and each pLTS at leaves having a finite number of states and
+(symbolic) transitions, has a finite automaton. The proof can be found
+in \cite{henrio:Forte2016}.
+
+\begin{theorem}[Finiteness of open-automata.]\\
 Given an open pNet $pnet=\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $l_i^{i\in L}$ and holes $h_j^{j\in

### 2019-03-25 2017-Xudong-SMT/ActaInformatica.tex
New proof for Th.2.

@@
 \begin{proof}
-
-Intuitively, $\forall \ostate{\tilde{s}}\in\textit{Explored}=State(L)\text{, there must exist a transition}\ostate{\tilde{s_i}}\xrightarrow{v_i}\ostate{\tilde{s}}\text{ and }\forall \ostate{\tilde{s}}\in\textit{Explored}_{Smart}=State(L_{Smart})\text{, }\exists\ostate{\tilde{pre(s)}}\text{, }\ostate{\tilde{pre(s)}}\xrightarrow{v}\ostate{\tilde{s}}\text{ where \textit{Pred} is satisfiable and the state}\ostate{\tilde{pre(s)}}\text{ has two cases:}$
+Let $L$, $L1$, $L_{Smart}$ respectively mean the result open transition set of original algorithm before pruning, original algorithm after pruning and smart algorithm.
+Similarly, $State(L)$, $State(L1)$, $State(L_{Smart})$ mean the result global state set of them.
+According to the algorithm, there has $L_{Smart}\in L$ and $State(L_{Smart})\in State(L)$.
+
+Suppose that $f$: $State(L1)\rightarrow State(L_{Smart})$.
 \begin{enumerate}
-	\item[(1)] $\ostate{\tilde{pre(s)}}=\ostate{\tilde{s}}$
-	\item[(2)] $\ostate{\tilde{pre(s)}}\in\textit{Explored}\text{-}\{\ostate{\tilde{s}}\}$
+\setlength{\itemindent}{3.5em}
+	\item[(Surjective)] If $\ostate{\tilde{s_0}}=Initial(p)$ then $f(\ostate{\tilde{s}})=\ostate{\tilde{t_0}}=Initial(p)$ must exists, the transitions started from them fulfill that
+	\[\forall \ostate{\tilde{t_0'}}, \ostate{\tilde{t_0}}\xrightarrow{v_j}\ostate{\tilde{t_0'}}\in L_{Smart},\quad \exists\ostate{\tilde{s'}},\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}\in L.\]
+	The state $\ostate{\tilde{t'}}\in State(L_{Smart})$ and as $Pred_j$ of $\ostate{\tilde{t}}\xrightarrow{v_j}\ostate{\tilde{t_0'}}$ is satisfiable, then if the $Pred_i$ of $\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}$ is also satisfiable, the state $\ostate{\tilde{s_0'}}$ is reachable in the original open automaton s.t.
+$\ostate{\tilde{s_0'}}\in State(L1)$, we can construct the mapping
+	\[f(\ostate{\tilde{s_0'}})=\ostate{\tilde{t_0'}}.\]
+	If the $Pred_i$ of $\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}$ is not satisfiable then two transitions are not matched and $\ostate{\tilde{s_0'}}\notin State(L1)$.
+
+	Let $\textit{Explored}$, $\textit{Explored}_{Smart}$ respectively mean the explored states set of original algorithm and smart algorithm.
+
+	Suppose that  $\ostate{\tilde{s}}\in \textit{Explored}$ there is $\ostate{\tilde{t}}\in \textit{Explored}_{Smart}$ where $f(\ostate{\tilde{s}})=\ostate{\tilde{t}}$, there exists a sequence of transitions $\ostate{\tilde{s_0}}...\xrightarrow{v_i}...\ostate{\tilde{s}}$ and $\ostate{\tilde{t_0}}...\xrightarrow{v_j}...\ostate{\tilde{t}}$.
+
+	The transitions $\ostate{\tilde{s}}\xrightarrow{v}\ostate{\tilde{s'}}$ and $\ostate{\tilde{t}}\xrightarrow{v}\ostate{\tilde{t'}}$ have several cases:
+	\begin{enumerate}
+		\item[(1)] $\ostate{\tilde{t'}}\in \textit{Explored}_{Smart}$
+
+		We can find that 
+		 \[\exists\ostate{\tilde{s'}}\in \textit{Explored},\quad \ostate{\tilde{s}}\xrightarrow{v}\ostate{\tilde{s'}}\quad where\quad f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}.\]
+		\item[(2)] $\ostate{\tilde{t'}}\notin \textit{Explored}_{Smart}$
+
+		There must has 
+		\[\exists\ostate{\tilde{s'}}\notin \textit{Explored},\quad \ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}.\]
+		If the $Pred_i$ of $\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$ is satisfiable then there exists a sequence of transitions $\ostate{\tilde{s_0}}...\xrightarrow{v_i}...\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$.
+So the $\ostate{\tilde{s'}}$ is reachable in the original open automaton, we can construct the mapping
+		\[f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}.\]
+		If the $Pred_i$ of $\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$ is not satisfiable then two transitions are not matched and $\ostate{\tilde{s'}}\notin State(L1)$.
 	\end{enumerate}	
-By induction, there must exists a sequence $\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s}}$ where all the $\textit{Pred}_i$ are satisfiable.
-
-Then $\forall\ostate{\tilde{t}}\textit{Explored}=State(L)$, there are also two cases:
-\begin{enumerate}
-	\item[(1)] $\ostate{\tilde{t}}\in State(L1)$
-
-	By definition of reachability, there exists a sequence $\ostate{\tilde{s_0}}...\xrightarrow{v_j}...\ostate{\tilde{t}}$ where all the $\textit{Pred}_j$ are satisfiable.
-
-	$\Rightarrow \ostate{\tilde{t}}\in State(L_{Smart})$
-	\item[(2)] $\ostate{\tilde{t}}\in State(L)\text{-}State(L1)$, then $\forall \ostate{\tilde{u}}\in\textit{Explored}-\{\ostate{\tilde{t}}\}$,
-	\begin{enumerate}
-		\item[(1)] $\ostate{\tilde{u}}\in State(L)\text{-}State(L1)$.
-		\item[(2)] $\ostate{\tilde{u}}\in State(L1)$, but there is no transition $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{t}}$.
-		\item[(3)] $\ostate{\tilde{u}}\in State(L1)$, there exists transition $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{t}}$, but the $\textit{Pred}_u$ is unsatisfiable.
+	Overall, \[\forall \ostate{\tilde{t}}\in State(L_{Smart}),\quad \exists\ostate{\tilde{s}}\in State(L1), f(\ostate{\tilde{s}})=\ostate{\tilde{t}}.\]
+	\item[(Injective)] If there is a pair of states $\ostate{\tilde{s}} and \ostate{\tilde{t}}$ constructs the mapping $f(\ostate{\tilde{s}})=\ostate{\tilde{t}}$.
+We can know that $\ostate{\tilde{s}}\in \textit{Explored},\ostate{\tilde{t}}\in \textit{Explored}_{Smart}$.
+
+	As when there is $\ostate{\tilde{t'}}\in \textit{Explored}_{Smart}$, the state is must be $\ostate{\tilde{s'}}\in \textit{Explored}$ where $f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}$.
+	So it is a one-to-one mapping.
 \end{enumerate}
-	By induction, there is no sequence from $\ostate{\tilde{s_0}}$ to $\ostate{\tilde{t}}$.
-
-	$\Rightarrow \ostate{\tilde{t}}\notin State(L_{Smart})$
-\end{enumerate}
-Overall, $State(L1)$ is equal to $State(L_{Smart})$.
+
+Then as the function $f$ is both surjective and injective, it is a bijective function. The theorem is proved.
+
+%Intuitively, $\forall \ostate{\tilde{s}}\in\textit{Explored}=State(L)\text{, there must exist a transition}\ostate{\tilde{s_i}}\xrightarrow{v_i}\ostate{\tilde{s}}\text{ and }\forall \ostate{\tilde{s}}\in\textit{Explored}_{Smart}=State(L_{Smart})\text{, }\exists\ostate{\tilde{pre(s)}}\text{, }\ostate{\tilde{pre(s)}}\xrightarrow{v}\ostate{\tilde{s}}\text{ where \textit{Pred} is satisfiable and the state}\ostate{\tilde{pre(s)}}\text{ has two cases:}$
+%\begin{enumerate}
+%	\item[(1)] $\ostate{\tilde{pre(s)}}=\ostate{\tilde{s}}$
+%	\item[(2)] $\ostate{\tilde{pre(s)}}\in\textit{Explored}\text{-}\{\ostate{\tilde{s}}\}$
+%\end{enumerate}
+%By induction, there must exists a sequence $\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s}}$ where all the $\textit{Pred}_i$ are satisfiable.
+%
+%Then $\forall\ostate{\tilde{t}}\textit{Explored}=State(L)$, there are also two cases:
+%\begin{enumerate}
+%	\item[(1)] $\ostate{\tilde{t}}\in State(L1)$
+%	
+%	By definition of reachability, there exists a sequence $\ostate{\tilde{s_0}}...\xrightarrow{v_j}...\ostate{\tilde{t}}$ where all the $\textit{Pred}_j$ are satisfiable.
+%	
+%	$\Rightarrow \ostate{\tilde{t}}\in State(L_{Smart})$
+%	\item[(2)] $\ostate{\tilde{t}}\in State(L)\text{-}State(L1)$, then $\forall \ostate{\tilde{u}}\in\textit{Explored}-\{\ostate{\tilde{t}}\}$,
+%	\begin{enumerate}
+%		\item[(1)] $\ostate{\tilde{u}}\in State(L)\text{-}State(L1)$.
+%		\item[(2)] $\ostate{\tilde{u}}\in State(L1)$, but there is no transition $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{t}}$.
+%		\item[(3)] $\ostate{\tilde{u}}\in State(L1)$, there exists transition $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{t}}$, but the $\textit{Pred}_u$ is unsatisfiable.
+%	\end{enumerate}
+%	By induction, there is no sequence from $\ostate{\tilde{s_0}}$ to $\ostate{\tilde{t}}$.
+%	
+%	$\Rightarrow \ostate{\tilde{t}}\notin State(L_{Smart})$
+%\end{enumerate}
+%Overall, $State(L1)$ is equal to $State(L_{Smart})$.
 \end{proof}

### 2019-03-26 2017-Xudong-SMT/ActaInformatica.tex
reformulated thms 2, 3

@@
 	such systems in a compositional manner. 
-	We propose and implement an algorithm computing these semantics,
+	We present an algorithm computing these semantics,
 	building predicates expressing the synchronisation conditions
@@
 %	behavioural properties such as safety and liveness.
-\ERIC{We also propose and implement an optimised
+We also propose and implement an optimised
 	algorithm that performs part of the pruning on-the-fly, and show 
-	this new algorithm is correct with respect to the original one.
+	its correctness with respect to the original one.
 	We illustrate the approach using two use-cases: the first one is a
@@
 	properties, and then show how our algorithms scale up, using a
-	composition of two such architectures.}}
+	composition of two such architectures.}
 
@@
 	\label{def:OpenTransitions}
-	An \emph{open transition} $OT$ over
+	An \emph{open transition} ($OT$) over
 	% a set  $\langle S_i,s_{0 i}, \rightarrow_i\rangle^{i\in I}$ of LTSs,
@@
 	is an action of the hole $j$, and $\alpha$ is the resulting action
-	of $OT$. \Pred\ is a predicate
+	of the $OT$. \Pred\ is a predicate
 	over the variables of the terms, labels, and states $s_i$,
@@
 If a pNet contains no assignment to state variables, then the smart
-algorithm, without final reachability computation, computes exactly
-the same open automaton as that of Algorithm 1.
+algorithm, without a final reachability computation, computes 
+the same open automaton as that of Algorithm 1 up to a renaming of  variables in the transitioin labels.
   \end{theorem}
@@
 In the general case, the smart
-algorithm, with a final reachability computation, computes exactly
-the same open automaton as that of Algorithm 1.
+algorithm, with a final reachability computation, computes 
+the same open automaton as that of Algorithm 1 up to a renaming of  variables in the transitioin labels.
 \end{theorem}
@@
 
-\section{pNet semantic rules}
+\section{Semantic Rules of pNets }
 \label{appendix:semRules}
 
-\paragraph{Note:} For convenience, we have included here the semantic rules for pNets,
-that were already published in \cite{henrio:Forte2016}.
+To facilitate the understanding of the two algorithms, we briefly recall the semantic rules of pNets, more details can be found in \cite{henrio:Forte2016}.
 
 We build the semantics of an open pNet as an open automaton where
-LTSs are the pLTSs at 
-the pNet leaves, and the states are structured as in
-the previous section. 
-To build an open transition one first
- projects the global state into states of the leaves, then applies
-pLTS transitions on these states, and compose them with actions of
+LTSs are the PLTSs at 
+the pNet leaves, and the states of the automaton are structured. 
+To build an open transition we first
+ projects the global state into states of the leaves, then apply
+PLTS transitions on these states, and compose them with actions of
 holes using synchronisation vectors.
@@
 fresh one.
-The variables in each synchronization vector are considered local:
+The variables in each synchronisation vector are considered local:
 for a given pNet expression, we must have fresh local variables for
-each occurrence of a vector (= each time we instantiate rule
-Tr2). Similarly the state variables of each copy of a
-given pLTS in the system, must be distinct, and those created for each
+each occurrence of a vector. %(= each time we instantiate rule Tr2). 
+Similarly, the state variables of each copy of a
+given PLTS in the system must be distinct, and those created for each
 application of Tr2 have to be fresh and all distinct.
@@
 
-  The rule ({\bf Tr1}) for a pLTS $p$  checks that the guard 
+  The first rule ({\bf Tr1}) for a PLTS $p$  checks that the guard 
   is verified and transforms assignments into post-conditions:
@@
   The second rule ({\bf Tr2}) deals with pNet nodes: for each possible
-  synchronization vector applicable to the rule subject, the premisses
+  synchronisation vector applicable to the rule subject, the premisses
   include one {\em open transition} for each sub-pNet involved, one possible
-  {\em action} for each Hole involved, and the predicate relating these
+  {\em action} for each hole involved, and the predicate relating these
   with the resulting action of the vector.
@@
   expressed in terms of the leaves and holes of the pNet structure,
-  i.e. a flatten view of the pNet: e.g. $L$ is the index set of the
-  Leaves, $L_k$ the index set of the leaves of one subnet, so all $L_k$
+  i.e. a flatten view of the pNet. For example, in the rule, $L$ is the index set of the leaves of the open pNet, $L_k$ is the index set of the leaves of one subnet, thus all $L_k$
   are disjoint subsets of $L$.
@@
 
-Within our algorithm, these subsets have been computed by the
+Within Algorithm~\ref{alg1}, these subsets have been computed by the
 $Combining$ method and passed as arguments to the $Matching$ method
-(see section~\ref{section:implementation})
-
-\paragraph{Termination.} To have some practical interest, it is important to know when this
-algorithm terminates. The following theorem shows that an open-pNet
-with finite synchronization sets, finitely many leaves and
-holes, and each pLTS at leaves having a finite number of states and
-(symbolic) transitions, has a finite automaton. The proof can be found
-in \cite{henrio:Forte2016}.
-
-\begin{theorem}[Finiteness of open-automata.]\\
-Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $pLTS_i^{i\in I}$ and holes $Hole_j^{j\in
-  J}$, if the sets $I$ and $J$ are finite, if the synchronization vectors of all pNets 
-  included in  $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ 
-  are finite, and if
-$\forall i \in I.\, finite{(states(pLTS_i))} \text{ and } pLTS_i$
-has a finite number of state variables, then Algorithm 1 terminates
-and produces an open automaton 
-$\mathcal{T}$ with finitely many states and transitions.
-
-\end{theorem}
-
+(cf. Section~\ref{section:implementation})
+
+To have some practical interest, it is important to know when Algorithm~\ref{alg1} terminates. The following theorem shows that if an open pNet
+has finite synchronisation sets, finitely many leaves and
+holes, and each PLTS at its leaves has a finite number of states and
+(symbolic) transitions, then Algorithm~\ref{alg1} terminates and the operational semantics of the open pNet is a finite automaton.
+
+\medskip
+\begin{theorem*}
+\noindent\textbf{Theorem 1 (Finiteness) }\cite{henrio:Forte2016}
+	Let $pnet=\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ be an open pNet  with leaves $l_i^{i\in I}$ and holes $h_j^{j\in
+		J}$, where the sets $I$ and $J$ are finite. Suppose the synchronisation vectors of all pNets 
+	included in  $pnet$   are finite, and 
+	% $\forall i \in L.\, finite{(states(l_i))} \text{ and } l_i$ 
+	$l_i $ has a finite number of state variables for each $i\in I$. Then the semantics of $pnet$ is an open automaton 
+	%$\mathcal{T}$ 
+	with finitely many states and transitions.
+\end{theorem*}
 \begin{proof}
-  The possible set of states of the open-automaton is the cartesian
-  product of the states of the pNet $pLTS_i^{i\in I}$, that is finite by
+  The possible set of states of the open automaton is the cartesian
+  product of the states of the pNet $PLTS_i^{i\in I}$, which is finite by
   hypothesis. So the top-level residual loop of Algorithm 1 terminates provided each 
-  iteration terminates. The enumeration of open-transitions in step 2b is bounded by the
-  number of applications of rules Tr2 on the structure of the
-  pNet tree, with a finite number of synchronisation vectors applying
-  at each node the number of global open transitions is finite. Similarily rule Tr1 is 
-  applied finitely if the number
-  of transitions of each pLTS is finite. So we get finitely many deduction trees, and
-  open-transitions which ensures that each internal loop of Algorithm 1 terminates.
+  iteration terminates. The enumeration of open-transitions in line 5 of Algorithm~\ref{alg1} is bounded by the
+  number of applications of rule Tr2 on the structure of the
+  pNet tree. Since a finite number of synchronisation vectors are applied
+  at each node, the number of global open transitions is finite. Similarily, if the number
+  of transitions of each PLTS is finite, rule Tr1 is 
+  applied a finite finite number of times. Therefore, each internal loop of Algorithm~1 terminates, and we obtain finitely many deduction trees and
+  open transitions.
+  \hfill \qed
   \end{proof}

### 2019-03-26 2017-Xudong-SMT/ActaInformatica.tex
biblio

@@
 As mentioned above, early attempts were made by Lin and others to define symbolic bisimulations for process calculi such as value-passing CCS and the $\pi$-calculus, and design algorithms to compute the most general condition under which two processes are bisimilar.
+The idea of symbolic semantics was also generalised to the setting of quantum CCS \cite{FDY14}.
 However, there is no algorithmic treatment of the symbolic systems developed by
@@
 calculus of broadcasting system (CBS). CBS is similar to classic
-process calculi such as CCS and CSP, but communicating by broadcasting
+process calculi such as CCS and CSP \cite{Hoa85}, but communicating by broadcasting
 values, %one-to-many communication instead of one-to-one communication and

### 2019-03-26 2016-Weak-FH-Bisim/WeakBisim.tex
lemma 6 proof in progress

@@
 \alpha'_n]$ is a a list of $\alpha_p$ such that $p\in [0..(n_1\!+\!n_2\!+\!2)] \land \alpha_p\neq \tau$ where for all $k\in [0\ldots n_1+n_2+2]$, $\beta_{kj_0}=\alpha_k$.
-In other words, $\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{i{j_0}}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{i{j_0}}} = [\alpha'_0..
-\alpha'_n]$.
+In other words, $\displaystyle{\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{i{j_0}}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{i{j_0}}} = [\alpha'_0..
+\alpha'_n]}$.
 This ensures that $\gamma_{j_0}=[\alpha'_0..
@@
 By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
-$ \forall i \in [0..m].\openrule
-    {
-       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
-         {s_{il}^{\, l\in L} \OTarrow {\tau} s_{(i+1)l}^{\, l\in L}} \in \mathcal{T} \quad \wedge
-\quad
-\openrule
-         {
-           \set{\beta^2},\Pred^2,\Post^2 }
-         {t_{l}^{\, l\in L} \OTarrow {\alpha} {t'}_{l}^{\,l\in L}} \in \mathcal{T}
-\quad \wedge\\
-\forall i \in [0..n].\openrule
-         {
-           \set{\beta^3_i},\Pred^3_i, \Post^3_i}
-         {v_{il}^{\, l\in L} \OTarrow {\tau} v_{(i+1)l}^{\, l\in L}} \in \mathcal{T}$ 
+$\forall p\!\in\![0..m].\openrule
+    {\set{\beta^1_p},\Pred^1_p,\Post^1_p   }
+         {\ostate{{(s^1_{pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s^1_{(p+1)i})}^{i\in L}}}\!\in\!\mathcal{T} \wedge
+\openrule
+         {\set{\beta^2},\Pred^2,\Post^2 }
+         {\ostate{({s_{0i}^2})^{i\in L}} \OTarrow {\alpha} \ostate{({s_{1i}^2})^{i\in L}}}\! \in\! \mathcal{T}
+\wedge\\
+\forall p \in [0..n].\openrule
+         {
+           \set{\beta^3_p},\Pred^3_p, \Post^3_p}
+         { \ostate{(s^3_{pi})^{i\in L}} \OTarrow {\tau} \ostate{(s^3_{(p+1)i})^{i\in L}}} \in \mathcal{T}$ 
 \\
 where for all $l\in L$:\\
-$s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
-$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i}}}\\
-\Pred=\bigwedge_{i=0}^{m_1}\!\big(\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land \bigwedge_{i=0}^{m_2}\!\Pred_i^3\big(\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\big)\\
-\Post=\bigotimes_{i=0}^{m_2}\Post^3_i\subst{\Post^2}\bigotimes_{j=0}^{m_1}\subst{\Post^1_j}
+$s_i=s^1_{0 i} \wedge s^1_{(m_1+1) i}=s^2_{0i} \wedge  s^2_{1i}= s^3_{0 i} \wedge s^3_{(m_2+1) l}=s'_i$\\
+$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{p=0}^{m_1} \vis{\set{\beta^1_p}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{p=0}^{m_2} \vis{\set{\beta^3_p}}}\\
+\Pred=\bigwedge_{p=0}^{m_1}\!\big(\Pred^1_p\bigotimes_{j=0}^{p-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{p=0}^{m_1}\subst{\Post_p^1}\land \bigwedge_{p=0}^{m_2}\!\Pred_p^3\big(\bigotimes_{j=0}^{p-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{p=0}^{m_1}\subst{\Post_p^1}\big)\\
+\Post=\bigotimes_{p=0}^{m_2}\Post^3_p\subst{\Post^2}\bigotimes_{j=0}^{m_1}\subst{\Post^1_j}
 $\\
-
 Moreover, we have for all $p\in[0..n]$:
-
 \begin{mathpar}
@@
 \end{mathpar}
-Also, by Lemma \ref{lem-rel-OT-WOT} this implies the following:\\
-$\forall k\! \in\! [0..m']\,\, Q\models{\openrule
-			{
-				(\beta^1_{kj})^{j\in J\cap\Holes(Q)}, {{\Pred_k^{1b}}},  
-				{{\Post_k^{1b}}}}
-				{\ostate{s_{kl}^{l\in L_Q}} \OTarrow {\tau}
-				\ostate{s_{(k+1)l}^{l\in L_Q}}}
+In the same way,  by Lemma \ref{lem-rel-OT-WOT} we can decompose $\WOT_p$ into  a series of $m'+n'$ tau open transitions and a single observable open transition:
+\[Q\models{\openrule
+			{
+				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred'^{2}}},  
+				{{\Post'^{2}}}}
+				{\ostate{s_{i}^{i\in L_Q}} \OTarrow {\alpha'_p}
+				\ostate{s_{i}'^{i\in L_Q}}}
 				}%\]
-,$ 
-$Q\models{\openrule
-			{
-				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred^{2b}}},  
-				{{\Post^{2b}}}}
-				{\ostate{s_{l}^{l\in L_Q}} \OTarrow {\alpha'_p}
-				\ostate{s_{l}'^{l\in L_Q}}}
-				}%\]
-$
-and
-$\forall k \in [0..n']\,\, Q\models{\openrule
-			{
-				(\beta^3_{kj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^{3b}}},  
-				{{\Post_p^{3b}}}}
-				{\ostate{s_{kl}^{l\in L_Q}} \OTarrow {\tau}
-				\ostate{s_{(k+1)l}^{l\in L_Q}}}
-				}%\]
-$\\ 
-Knowing that we have $j_0\in J$ and $\gamma_{j_0}=[\beta_0..\beta_n]$:
-Suppose that $Q$ moves in transition $\alpha$, then there is  a matching $p_0$ transition for some $p_0\in[0..n]$. 
-\[ P[Q]_{j_0}  
-	\models
-	{\openrule
-		{
-			(\beta^2_j)^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
-			\Pred^2\land\Pred^{2b}\land \alpha'_{p_0}=\beta^2_{j_0},  
-			\Post^2\uplus \Post^{2b}}
-		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {\alpha}
-			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
-	}
 \]
-NOTE: And $\beta^2_{j_0}= \beta_{p_0}$.
-
-Moreover, for each:
-$\openrule
-         {
-           \set{\beta_i},\Pred_i, \Post_i}
-         {s_i \OTarrow {\tau} s_{i+1}} \in \mathcal{T}$
+We can apply Lemma \ref{lem-compose} on each   $\symb{OT}_p$ of $P$ in the form: 
+$P\!\models		
+\openrule
+    {
+       {\beta_p^{p\in J}},\Pred_p,\Post_p   }
+         {\ostate{s^{i\in L}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L}_{(p+1)i}}}$ 
+\begin{enumerate}
+\item If $Q$ moves meaning that we have $Q\!\models		
+\openrule
+    {
+       {\beta_p^{p\in J_Q}},{\Pred_p}\!\!',{\Post_p} \!\!'  }
+         {\ostate{s^{i\in L}_{pi}} \OTarrow {\alpha_p'} \ostate{s^{i\in L}_{(p+1)i}}}$ and having that there exists $j_0\in J$ such that $\alpha'_p=\beta_{j_0}$ then  by Lemma \ref{lem-compose} we obtain:\\
+\[P[Q]_{j_0}\!\models		
+\openrule
+    {
+       \beta_p^{(p\in J\setminus\{j_0\}) \uplus J_Q},{\Pred_p}\!\!'',{\Post_p}\!\!''   }
+         {\ostate{s^{i\in L \uplus L_Q}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L\uplus L_Q }_{(p+1)i}}}\] \\
+ such that  ${\Pred_p}\!\!'' \iff {\Pred_p}
+		\land {\Pred_p}\!\!'\land \alpha_p'=\beta_{j_0}$, ${\Post_p}\!\!''={\Post_p}\uplus 
+		{\Post_p}\!\!'$ 
+		\item Else $Q$ does not move, i.e. we have: $\ostate{(s_{pi})^{i\in L_Q}} = \ostate{({s}_{(p+1)i})^{i\in L_Q}}$. By Definition \ref{def:Non-ObsTau} we write:
+
+		\[ Q\!\models \openrule
+         {
+           (j\mapsto\tau),\True,\Id(s_{pi})}
+         { \ostate{s^{i\in L}_{pi}} \OTarrow {\tau}\ostate{s^{i\in L}_{pi}}}\]
+So we obtain by Lemma \ref{lem-compose}:
+\[P[Q]_{j_0}\!\models		
+\openrule
+    {
+       \beta_p^{(p\in J\setminus\{j_0\}) \uplus J_Q},{\Pred_p}\!\!',  {\Post_p}\!\!' }
+         {\ostate{s^{i\in L\uplus L_Q}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L\uplus L_Q}_{(p+1)i}}}\] \\
+\end{enumerate}
+Therefore we  obtain a series of $m+n$ tau open transitions and a single observable open transition. Thus by Lemma \ref{lem-rel-OT-WOT} that implies we have:
+\[P[Q]_{j_0}\!\models		
+\openrule
+    {
+       \beta_p^{(p\in J\setminus\{j_0\}) \uplus J_Q}, {\Pred_p}
+		\land {\Pred_p}\!\!'\land \alpha_p'=\beta_{j_0}$, ${\Post_p}\!\!''={\Post_p}\uplus 
+		{\Post_p}\!\!'}
+         {\ostate{s^{i\in L\uplus L_Q}_{pi}} \OTWeakarrow {\alpha} \ostate{s^{i\in L \uplus L_Q}_{(p+1)i}}}\] 
 \qed

### 2019-03-26 2017-Xudong-SMT/ActaInformatica.tex

@@
 %% There is not much research work towards trying 
-As mentioned above, early attempts were made by Lin and others to define symbolic bisimulations for process calculi such as value-passing CCS and the $\pi$-calculus, and design algorithms to compute the most general condition under which two processes are bisimilar.
-The idea of symbolic semantics was also generalised to the setting of quantum CCS \cite{FDY14}.
+As mentioned above, early attempts were made by Lin and others to
+define symbolic bisimulations for process calculi such as
+value-passing CCS and the $\pi$-calculus, and design algorithms to
+compute the most general condition under which two processes are
+bisimilar \cite{HennessyLin:TCS95,Linconcur96,APSEC::Lin2001}. The idea of symbolic semantics was also generalised to the setting of quantum CCS \cite{FDY14}. 
 However, there is no algorithmic treatment of the symbolic systems developed by
@@
 classic works.
+
+From a broader perspective, after the seminal work
+of Hennessy, Lin, and their colleagues on value-passing systems with
+assignments, many
+different works addressing various classes of infinite-state systems
+and/or parameterised topologies have been published, using
+combinations of approaches, often including predicate abstraction and
+SMT satisfiability (\eg \cite{DBLP:journals/jsat/AlbertiGPRR12,BruniEtAl-Tiles-Concur2000,CimattiEtAl-NUXMV-CAV2014,ChampionEtAl-Kind2-CAV2016,DBLP:conf/cade/GhilardiNRZ08}). With
+respect to these, we use symbolic representations not only to get a
+finite representation of infinite spaces, but also to express the
+(data-sensitive) synchronisations with the environment, making our
+models suitable for compositional verification.
+Among these works, several have shown the capacity of the SMT engines
+(either Z3 or Yikes) as servers for solving verification conditions of
+the algorithms, for large case-studies
+(\eg
+\cite{DBLP:journals/corr/abs-1806-11459,DBLP:journals/corr/CimattiGMT13}).
 
@@
 algorithm, without a final reachability computation, computes 
-the same open automaton as that of Algorithm 1 up to a renaming of  variables in the transitioin labels.
+the same open automaton as that of Algorithm 1 up to a renaming of
+variables in the transition labels.  
   \end{theorem}
-
-\TODO{Need to refine theorem, and to check the proof... To answer
-  Yuxin question about ``exactly the same'', indeed it is not
-  correct... But not for states: state labels will be exactly the
-  same. But transitions will not, because of the mechanism for
-  generating fresh variables; so we may need to reword as ``bijective''}
 
@@
 algorithm, with a final reachability computation, computes 
-the same open automaton as that of Algorithm 1 up to a renaming of  variables in the transitioin labels.
+the same open automaton as that of Algorithm 1 up to a renaming of  variables in the transition labels.
 \end{theorem}
@@
 Figure~\ref{schema:smt-lib} shows the translation of  Figure~\ref{schema:unsat-ot}
-in the SMTlib syntax.
-\TODO{Change the text: DONE}It contains the declaration
+in the SMTlib syntax. It contains the declaration
 of the relevent part of the Lotos action algebra sorts 
@@
 \begin{figure}[t]
-  %  \centerline{\includegraphics[width=12cm]{XFIG/SMTLIB2}}
     \centerline{\includegraphics[width=0.8\linewidth]{ActaXFIG/rise4fun1}}
@@
 \centerline{ 
-  \includegraphics[width=0.30\linewidth]{ActaXFIG/Enable1}
+  \includegraphics[width=0.30\linewidth]{ActaXFIG/Enable1-aut}
   \hspace{25mm}
-  \includegraphics[width=0.25\linewidth]{ActaXFIG/Enable2}}
+  \includegraphics[width=0.25\linewidth]{ActaXFIG/Enable2-aut}}
   \begin{minipage}{5.7cm}
@@
 Figure~\ref{schema:enable-pnets} are displayed in
-Figure~\ref{schema:enable-OAs}. We have shown in \cite{henrio:Forte2016} how to
+Figure~\ref{schema:enable-OAs}.
+Note that although these automata look very similar to the pLTS
+controlers from Figure~\ref{schema:enable-pnets}, their nature is very
+different: they represent the behavior of the whole system, including
+the holes $P$ and $Q$. Their transitions do not rely on a particular
+implementation of the controlers, but only encode the logical
+relations between the actions of the holes.
+
+We have shown in \cite{henrio:Forte2016} how we can
 prove that these two automata are bisimilar.
@@
 %%\subsection{simple communication protocol} specification and implementation;
-\TODO{Eric: more results: enable associativity}
+%%\TODO{Eric: more results: enable associativity}
+
+\medskip
+Now if we look at the Enable composition from
+Figure~\ref{schema:enable-composed}, its open automaton is shown in
+Figure~\ref{schema:enable3bis}. Building the symetric system ``(P>>Q)>>R'' in a similar
+way will allow us to prove that they are bisimilar (the Enable
+operator is associative), as we have shown in \cite{HMZ:RR-2016}.
+This approach allows us to study the equational properties of
+many classical process algebra or parallel languages operators, even
+when their semantics depends on data properties.
+
+\begin{figure}[h]
+  \begin{minipage}{2cm}
+  \includegraphics[width=\linewidth]{ActaXFIG/PQR-automaton}
+  \end{minipage}
+  \hspace{10mm}
+  \begin{minipage}{7cm}
+  \begin{eqnarray*}
+    OT_1 & = \openrule{\{\xrightarrow{a1}_P\}\\ a1\neq\delta(x)}
+    {\ostate{00} \xrightarrow{a1} \ostate{00}}\\
+    OT_2 & = \openrule{
+                            \{\xrightarrow{\delta(x1)}_P, ~~
+                            \xrightarrow{acc(x1)}_Q\}
+                      }
+                      {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}    \\
+    OT_3 & = \openrule{
+                        \{\xrightarrow{a2}_Q\},\\a2\neq\delta(x)
+                        }
+    {\ostate{10} \xrightarrow{a2} \ostate{10}}\\
+    OT_4 & = \openrule{
+                      \{\xrightarrow{\delta(x2)}_Q, \qquad 
+                       \xrightarrow{acc(x2)}_R\} 
+                       }
+                      {\ostate{10} \xrightarrow{\underline{\delta(x2)}} \ostate{11}}    \\
+    OT_5 & = \openrule{\{\xrightarrow{a3}_R\}
+    	}
+    {\ostate{11} \xrightarrow{a3} \ostate{11}}
+    \end{eqnarray*}
+  \end{minipage}
+  \caption{Open Automaton for the term ``P>>(Q>>R)''}
+  \label{schema:enable3bis}
+\end{figure}
 
@@
 \medskip
-\begin{theorem*}
+\begin{theorem}
 \noindent\textbf{Theorem 1 (Finiteness) }\cite{henrio:Forte2016}
@@
 	with finitely many states and transitions.
-\end{theorem*}
+\end{theorem}
 \begin{proof}

### 2019-03-26 2016-Weak-FH-Bisim/WeakBisim.tex
essai de changement de titre
Work on skype

@@
 
-\title{More equivalences for Open pNets\thanks{This work was partially 
+\title{Compositional equivalences based on Open pNets\thanks{This work was partially 
 funded by the Associated Team FM4CPS
@@
 By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
-$\forall p\!\in\![0..m].\openrule
+$\forall p\!\in\![0..m_1].\openrule
     {\set{\beta^1_p},\Pred^1_p,\Post^1_p   }
@@
 \wedge\\
-\forall p \in [0..n].\openrule
+\forall p \in [0..m_2].\openrule
          {
@@
 \\
-where for all $l\in L$:\\
-$s_i=s^1_{0 i} \wedge s^1_{(m_1+1) i}=s^2_{0i} \wedge  s^2_{1i}= s^3_{0 i} \wedge s^3_{(m_2+1) l}=s'_i$\\
+where for all $i\in L$:\\
+$s_i=s^1_{0 i} \wedge s^1_{(m_1+1) i}=s^2_{0i} \wedge  s^2_{1i}= s^3_{0 i} \wedge s^3_{(m_2+1) i}=s'_i$\\
+
 $\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{p=0}^{m_1} \vis{\set{\beta^1_p}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{p=0}^{m_2} \vis{\set{\beta^3_p}}}\\
@@
 $\\
+
+Note: If $(\beta^i_p)_{j_0}=\tau$ Because of Definition 11, $P$ necessarily do a $\tau$ open transition and remains in the same state, ($s_p = s_{p+1}$).
+Thus without loss of generality, we can bypass such an open transition and obtain another decomposition of the WOT without the open transition that requires $({\beta^i_p})_{j_0}=\tau$.
+We can thus  suppose that for all $p$ and $i$ we have $({\beta^i_p})_{j_0}\neq\tau$.
+
 Moreover, we have for all $p\in[0..n]$:
@@
 				{{\Post'^{2}}}}
-				{\ostate{s_{i}^{i\in L_Q}} \OTarrow {\alpha'_p}
+				{\ostate{s_{i}^{i\in L_Q}} \OTarrow {\alpha_p}
 				\ostate{s_{i}'^{i\in L_Q}}}
@@
     {
-       {\beta_p^{p\in J}},\Pred_p,\Post_p   }
+       {(\beta^i_p)^{p\in J}},\Pred_p,\Post_p   }
          {\ostate{s^{i\in L}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L}_{(p+1)i}}}$
+
+au depart sQ0
+
+pour chaque etape de P
+- si $j_0\in J$ alors on fait une transition de Q, par definition $\beta^i_{j_0}=\beta_t$ with $\beta^i_{j_0}\neq \tau$ pour un certain t (t vaut 0 au debut et est incremente a chaque fois qu on passe dans cette condition).
+Dans ce cas, Q est dans l etat $s_{t Q}$ avec au depart $s_{0 Q}$ qui est l etat initial de Q avant la premiere OT de Q
+
+(t et p c est un peu la meme chose)
+
+donc on peut faire la transition numero t de Q (WOT)
+ on la decompose by Lemma \ref{lem-rel-OT-WOT}
+on a une famille d'OT
+
+k $\tau$
+$s'_h \OTarrow {\tau} s'_{h+1}$
+
+\[Q\models{\openrule
+			{
+				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred'^{2}}},  
+				{{\Post'^{2}}}}
+				{\ostate{s_{i}^{i\in L_Q}} \OTarrow {\alpha_p}
+				\ostate{s_{i}'^{i\in L_Q}}}
+				}%\]
+\]
+
+k' $\tau$
+$s''_h \OTarrow {\tau} s''_{h+1}$
+
+On commence par les $k$ premiers $\tau$
+On applique Def 11 pour dire que 
+P peut faire des transitions ou l etat de P ne bouge pas et le trou $j_0$ fait tau (le reste ne fait rien).
+Par le lemme 2 on compose P qui laisse passer un tau et Q qui fait tau on obtient une OT tau de P[Q].
+Finalement l'etat de Q atteint $s'_k$ avec
+$s'_k = \ostate{s_{i}^{i\in L_Q}}$. (A)
+
+La on peut faire l'OT  $\OTarrow {\alpha_p}$
+par le lemme 2 on compose les OT $\OTarrow {\alpha_p}$ et $\OTarrow {\alpha}$ on obtient un OT $\alpha$ pour P[Q] avec la condition $\alpha_p=\beta_{j_0}$ (dans le Pred du lemma 2). (B)
+
+On termine par les $k'$ derniers $\tau$
+On applique Def 11 et le lemme 2 comme au dessus pour dire que 
+P[Q] peut faire des OT tau ou l etat de P ne bouge pas et l'etat de Q atteint $s''_{k'}$ avec
+${s''}_{k'} = \ostate{(s'_{i})^{i\in L_Q}}$. (C)
+
+en composant (A) (B) et (C) on obtient une WOT k tau, 1 aplha et k' tau pour le pNet P[Q]
+
+$t$ incremente et $s_t$ devient $\ostate{(s'_{i})^{i\in L_Q}}$
+
+- sinon $j_0\not\in J$ : t ne bouge pas, l'etat de Q ne bouge pas (Q ne fait rien) on a la meme OT pour P[Q] que pour P
+
 \begin{enumerate}
-\item If $Q$ moves meaning that we have $Q\!\models		
+\item
+
+ If $Q$ moves meaning that we have $Q\!\models		
 \openrule

### 2019-03-26 2017-Xudong-SMT/ActaInformatica.tex
minor changes

@@
 combinations of approaches, often including predicate abstraction and
-SMT satisfiability (\eg \cite{DBLP:journals/jsat/AlbertiGPRR12,BruniEtAl-Tiles-Concur2000,CimattiEtAl-NUXMV-CAV2014,ChampionEtAl-Kind2-CAV2016,DBLP:conf/cade/GhilardiNRZ08}). With
+SMT satisfiability (\eg \cite{DBLP:journals/jsat/AlbertiGPRR12,BruniEtAl-Tiles-Concur2000,CimattiEtAl-NUXMV-CAV2014,ChampionEtAl-Kind2-CAV2016,DBLP:conf/cade/GhilardiNRZ08}). 
+Among these works, several have shown the capacity of the SMT engines
+(either Z3 or Yikes) as servers for solving verification conditions of
+ algorithms, for large case-studies
+(\eg
+\cite{DBLP:journals/corr/abs-1806-11459,DBLP:journals/corr/CimattiGMT13}).
+With
 respect to these, we use symbolic representations not only to get a
@@
 models suitable for compositional verification.
-Among these works, several have shown the capacity of the SMT engines
-(either Z3 or Yikes) as servers for solving verification conditions of
-the algorithms, for large case-studies
-(\eg
-\cite{DBLP:journals/corr/abs-1806-11459,DBLP:journals/corr/CimattiGMT13}).
 
@@
 %Strictly speaking, the LTSs at the leaves of the
-%open automaton are a restricted form of pLTSs, where labels are
+%open automaton are a restricted form of PLTSs, where labels are
 %parametrised actions, but include no guard nor assignments.
@@
 Figure~\ref{schema:enable-OAs}.
-Note that although these automata look very similar to the pLTS
-controlers from Figure~\ref{schema:enable-pnets}, their nature is very
+Note that although these automata look very similar to the PLTS
+controllers from Figure~\ref{schema:enable-pnets}, their nature is very
 different: they represent the behavior of the whole system, including
 the holes $P$ and $Q$. Their transitions do not rely on a particular
-implementation of the controlers, but only encode the logical
+implementation of the controllers, but only encode the logical
 relations between the actions of the holes.
-
-We have shown in \cite{henrio:Forte2016} how we can
-prove that these two automata are bisimilar.
+We have shown in \cite{henrio:Forte2016} how to prove these two automata are bisimilar.
 
@@
 
-\medskip
-Now if we look at the Enable composition from
-Figure~\ref{schema:enable-composed}, its open automaton is shown in
-Figure~\ref{schema:enable3bis}. Building the symetric system ``(P>>Q)>>R'' in a similar
+Now let us revisit the Enable composition from
+Figure~\ref{schema:enable-composed}. Its open automaton is shown in
+Figure~\ref{schema:enable3bis}. Building the symmetric system ``(P>>Q)>>R'' in a similar
 way will allow us to prove that they are bisimilar (the Enable
@@
 This approach allows us to study the equational properties of
-many classical process algebra or parallel languages operators, even
+many operators in classical process algebras or parallel languages, even
 when their semantics depends on data properties.
@@
 reset, unless a resumption is registered within $\mathrm{Max}$ time
-units (more details in Secion.~\ref{section:FailureTimer}).
+units (more details in Secion~\ref{section:FailureTimer}).
 
@@
 %% To improve the readability of this figure, we used the following conventions:
-%% we omit the transitions of the two pLTS, and the set of ``working''
+%% we omit the transitions of the two PLTS, and the set of ``working''
 %% holes; and we directly write the resulting action as first element of
@@
 \medskip
-\begin{theorem}
-\noindent\textbf{Theorem 1 (Finiteness) }\cite{henrio:Forte2016}
+\begin{theorem}[Finiteness]\cite{henrio:Forte2016}
+%\noindent\textbf{Theorem 1} 
 	Let $pnet=\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ be an open pNet  with leaves $l_i^{i\in I}$ and holes $h_j^{j\in

### 2019-03-26 2017-Xudong-SMT/ActaInformatica.tex
prof 2 and th 3

--- 2019-03-26 2017-Xudong-SMT/ActaInformatica.tex
@@
 \State \QIN{$\mathit{L1}$ = \texttt{filterUnsatTransitions}($\mathit{L,Assignements}$)}
-\State \QIN{$\mathit{OA}$ = \texttt{makeReachableSubAutomaton}($\mathit{InitState}(P)$,$\mathit{L1}$)}
-\State \Return $\mathit{OA}$;
+\State \QIN{$\mathit{OA1}$ = \texttt{makeReachableSubAutomaton}($\mathit{InitState}(P)$,$\mathit{L1}$)}
+\State \Return $\mathit{OA1}$;
 
@@
 
-\subsection{Management of State Variable Assignments}
+\subsection{Management of State Variables and Assignments}
 
@@
 list of assignment expressions for each PLTS state. 
-\QIN{The only assignments for state variables that happen at the PLTS level are as follows: every time the MakeTransitions
-algorithm is applied on a PLTS, it collects the expressions from the $Post$ in each transition.
+The only assignments for state variables that happen at the PLTS level
+are as follows: every time the MakeTransitions 
+algorithm is applied on a PLTS, it collects the expressions from the
+$Post$ in each transition. 
 % As there is no assignments collecting work on a pNet node, it is not
 % shown in Algorithm~\ref{alg2}.
-}
 
@@
 global state. \ERIC{The final assignment sets are assembled when building the
-open automaton from the reachable transitions.}
+open automaton from the reachable transitions, see below.}
 
@@
 
+Function \texttt{filterUnsatTransitions}, in line 11 of
+Algorithm\ref{alg1} makes use of the Z3 engine to implement the
+satisfiability checking, for all the OTs computed that far, and
+returns the set $L1$ of satisfiable OTs.
+
+\subsection{Building the Open Automaton}
+
+\ERIC{The set $L1$ may contain unreachable transitions, the last step of the
+algorithm builds the final Open Automaton as a traversal of $L1$,
+starting at the initial state $InitState(p)$ as defined in
+page~\pageref{def-states}. More precisely, this is a residual
+algorithm building a graph from transitions in $L1$, and states are
+the set of target states of transitions in $L1$, plus the initial
+states. Each state in the graph is decorated with a set of its local
+variables, and a list of their possible assignments,
+gathered during the traversal using the ``Post'' parts of the
+OTs.}
+
+\ERIC{A further reduction may now be gained by using the information from
+these sets of possible assignments: adding this information when
+checking satisfiability of transitions leaving a given state may
+result in more Unsat transitions: the set of possible
+assignments computed by the algorithm is an over approximation of
+possible values of the 
+variables of such state, so narrowing it means we get a better
+approximation, and potentially more information, which can be used in
+the SAT checking of subsequent transitions. In turn this may reduce the possible
+assignments of the corresponding target states. In theory we should
+iterate this procedure, each iteration reducing the set of
+transitions, and the sets of assignments; the final Open Automaton
+would be the fix point of this iteration. In practice this would be
+expensive, and it is not incorrect to leave some Unsat OTs in the
+result; in practical cases, very little will be gained computing the
+fixpoint, so we only perform one step. Further algorithms 
+(e.g. model-checking or equivalence checking) will be able to use the
+full information from the predicates and the assignment sets.}
+
 \subsection{Computing Reachable State Space on the Fly}
 
-\ERIC{The basic algorithm from the previous section potentially explores some
+The basic algorithm from the previous section potentially explores some
 areas of the global state-space that will not be reachable after
@@
 not the transitions issued from non-reachable global states. We use
-this idea to create our ``smart'' algorithm.}
+this idea to create our ``smart'' algorithm.
 
@@
   transitions, reachability is not as easy to define as in standard
-  models. As mentionned above, we collect all
-possible (symbolic) assignments of state variables, in the
-computed open automaton. By avoiding building the OTs coming from
-some unreachable states, we also avoid adding the corresponding assignments
-to the variables of their target states. The set of possible
-assignments computed by the algorithm is an over approximation of
-possible values of the 
-variables of such state, so narrowing it means we get a better
-approximation, and potentially more information, which can be used in
-the SAT checking of subsequent transitions. But we \emph{cannot} use this
+  models, as illustrated by the definition above. By avoiding building
+  the OTs coming from some unreachable states, we also avoid adding
+  the corresponding assignments to the variables of their target states.
+But we \emph{cannot} use the
 assignment information in the ``on-the-fly'' SAT checking, because
 they cannot be complete before exploring (at least) all the reachable
-state space. So the smart algorithm proceeds in two steps: during the
+state space. We first need to compute a first over-approximation of
+the reachable state space, and assignment sets; this corresponds to
+the set of OTs $L2$ in Algorithm~\ref{alg3}, line 15.
+So the smart algorithm proceeds in two steps: during the
 first step, the SAT checking is done without using any assignment set
 information. Then after the completion of this step, we perform another
-SAT checking of all transitions from step1, but this time using the
-assignment information. This may reduce the reachable state space. If
-we want to be sure that the obtained automaton is minimal, we should
-iterate this step until a fixed point is reached. But in practical cases, very
-little will be gained, so the default implementation does only one
-step. Leaving some UNSAT transitions in the
-symbolic automaton is still logically correct.
+SAT checking of all transitions from step1, using the
+assignment information, in the same way it is done at the end of
+Algorithm~\ref{alg1}.
+
+There is one case much simpler, that is when the pNets contains no
+state variable assignment. Then the set of transitions computed
+on-the-fly is already guaranted to be the final reachable set (line 13).
 
@@
 \IfThenElse {(NonEmptyAssignmentSet($\mathit{L}$))}
-        {\State \quad\ \Return $\mathit{OA}$=makeAutomaton($\mathit{InitState}(P),L)$;}
-        {\State \quad\ $\mathit{L1}$=filterUnsatTransitions($\mathit{L,Assignments}$);
-         \State \quad\ \Return $\mathit{OA}$=makeReachableSubAutomaton($\mathit{InitState}(P),L1)$};
+        {\State \quad\ \Return $\mathit{OA2}$=makeAutomaton($\mathit{InitState}(P),L)$;}
+        {\State \quad\ $\mathit{L2}$=filterUnsatTransitions($\mathit{L,Assignments}$);
+         \State \quad\ \Return $\mathit{OA2}$=makeReachableSubAutomaton($\mathit{InitState}(P),L2)$};
 \end{algorithmic}  
@@
 variables. This does not mean ``data-independency'': we can still have
-guards in the PLTS transitions and in the synchronisation vectors,
+guards in the pLTS transitions and in the synchronisation vectors,
 making the behaviour depending on the value of input variables. But
@@
 \begin{proof}
+  Let $pn=<...>$ be a pNet. The set of states 
+  managed by the two algorithms both are subsets of the cartesian
+  product of the pLTS states, as defined in \pageref{def-states}. In a
+  similar way, the set of state variables are also the same. Comparing
+  transitions requires a little more care, because within the
+  MakeTransitions function, fresh variables are created everytime a
+  synchronisation vector is used (this occurs within the $MkPred$ and
+  $matching$ functions). However, given a global state, the call of
+  $MakeTransitions$ will always returns the same set of OTs, up to
+  renaming of these fresh variables.
+
+  Let us define the following sets of OTs, as computed by the 2
+  algorithms:
+  \begin{itemize}
+    \item $L$ = original set of transitions by Algorithm 1, before pruning
+      (i.e. before line 11),
+    \item $L1-reach$ = final set of OTs of Algorithm 1, as computed
+        by line 12.
+      \item $L2-reach$ = final set of OTs of Algorithm 2, as computed
+          by line 13.
+  \end{itemize}
+
+  For each of these, define $States : OT^* -> State^*$ the function
+  computing the set of target states of a set of OTs.
+
+  We want to prove that $L1-reach = L2-reach$ (upto renaming of fresh
+  variables) and $States(L1-reach) = States(L2-reach)$.
+
+  Now remark that without assignments,
+  Theorem~\ref{Th:CorrectnessWithoutAssignments} boils to proving
+
 Let $L$, $L1$, $L_{Smart}$ respectively mean the result open transition set of original algorithm before pruning, original algorithm after pruning and smart algorithm.
@@
   checking. Still, the smart strategy will explore a reduced state
-  space, not necessarily the minimal one (discussion later).
+  space, not necessarily the minimal one (discussion later). In the
+  following theorem, both algorithm are considered in their complete
+  version, meaning the reachability (with assignments) step is
+  iterated up to fixpoint.
 
@@
   \label{Th:CorrectnessWithAssignments}
-In the general case, the smart
-algorithm, with a final reachability computation, computes 
+In the general case, the smart algorithm computes 
 the same open automaton as that of Algorithm 1 up to a renaming of  variables in the transition labels.

### 2019-03-26 2016-Weak-FH-Bisim/WeakBisim.tex

@@
 	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
-	\set{\symb{SV}}\myrangle$.
+	\set{\symb{SV}}\myrangle$ that cannot observe silent actions.
 	Let $j_0\in J$ be a hole. Let $\pNetQ$ and $Q'$ be two weak FH-bisimilar pNets such that 
@@
 	J}, 	\set{\symb{SV'}}\myrangle$ that are weak FH-bisimilar
-	(recall they must have the same holes to be bisimilar).
+	(recall they must have the same holes to be bisimilar) and that cannot observe silent actions.
 	Let $j_0\in J$ be a hole, and $\pNetQ$ be a pNet such that $\Sortop(\pNetQ)=\Sort_{j_0}$. Then 
@@
 \begin{theorem}[Composability of weak bisimulation]\label{weak-compos}
-	Consider two weak FH-bisimilar pNets with an arbitrary number of holes, when replacing, 
+	Consider two weak FH-bisimilar pNets with an arbitrary number of holes, such that the two pNets cannot observe silent actions. When replacing, 
 	inside those two original pNets, a subset of the holes by weak FH-bisimilar pNets, we 
@@
 
-\begin{lemma}[Weak open transition composition]\label{lem-compose} 
+\begin{lemma}[Weak open transition composition]\label{lem-compose} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
 	Suppose $j_0\in J$ and $\gamma_{j_0}=[\beta_0..\beta_n]$ and additionally:\\[-2ex]

### 2019-03-27 2017-Xudong-SMT/ActaInformatica.tex
Sketch of the proofs

@@
 
+\ERIC{Sketch of the proof:}
+
 \begin{proof}
@@
   product of the pLTS states, as defined in \pageref{def-states}. In a
-  similar way, the set of state variables are also the same. Comparing
+  similar way, the set of state variables are also equal. Comparing
   transitions requires a little more care, because within the
@@
   $matching$ functions). However, given a global state, the call of
-  $MakeTransitions$ will always returns the same set of OTs, up to
-  renaming of these fresh variables.
+  $MakeTransitions$ will always returns exactly the same set of OTs, up to
+  renaming of these fresh variables\footnote{I think this does not
+    need any specific proof, given that it is the same function,
+    called with the same arguments}.
 
@@
   algorithms:
+  \ERIC{not sure whether all these sets are useful, but it's good to
+    have them precisely defined for the moment}
   \begin{itemize}
-    \item $L$ = original set of transitions by Algorithm 1, before pruning
+    \item $L1$ = original set of transitions by Algorithm 1
       (i.e. before line 11), 
+    \item $L1-sat$ = original set of transitions by Algorithm 1, after
+      satisfiability check (i.e. after line 11),
     \item $L1-reach$ = final set of OTs of Algorithm 1, as computed
       by line 12.
+    \item $L2-sat$ = original set of transitions by Algorithm 2
+      (i.e. before line 13), 
     \item $L2-reach$ = final set of OTs of Algorithm 2, as computed
@@
 
-  Now remark that without assignments,
-  Theorem~\ref{Th:CorrectnessWithoutAssignments} boils to proving
-
-Let $L$, $L1$, $L_{Smart}$ respectively mean the result open transition set of original algorithm before pruning, original algorithm after pruning and smart algorithm.
+  From the structure of the main loops of the algorithms, we know that
+  $L1-sat \subset L2-sat$ and subsequently $States(L1-sat) \subset       
+  States(L2-sat)$.
+  \qed
+\end{proof}
+
+    \medskip
+  \noteInEM{I keep below the original proof draft from Xudong, though
+    I'm not sure if parts of it can be reused}
+\begin{proof}
+%% Let $L$, $L1$, $L_{Smart}$ respectively mean the result open transition set of original algorithm before pruning, original algorithm after pruning and smart algorithm.
 Similarly, $State(L)$, $State(L1)$, $State(L_{Smart})$ mean the result global state set of them.
@@
 
-Suppose that $f$: $State(L1)\rightarrow State(L_{Smart})$.
+We will construct a mapping $f$: $State(L1-reach)\rightarrow
+State(L2-reach)$.
+\ERIC{I do not understand this, as states are identical. You would
+  rather need mapping betwen transitions ?}
 \begin{enumerate}
@@
 
-%Intuitively, $\forall \ostate{\tilde{s}}\in\textit{Explored}=State(L)\text{, there must exist a transition}\ostate{\tilde{s_i}}\xrightarrow{v_i}\ostate{\tilde{s}}\text{ and }\forall \ostate{\tilde{s}}\in\textit{Explored}_{Smart}=State(L_{Smart})\text{, }\exists\ostate{\tilde{pre(s)}}\text{, }\ostate{\tilde{pre(s)}}\xrightarrow{v}\ostate{\tilde{s}}\text{ where \textit{Pred} is satisfiable and the state}\ostate{\tilde{pre(s)}}\text{ has two cases:}$
-%\begin{enumerate}
-%	\item[(1)] $\ostate{\tilde{pre(s)}}=\ostate{\tilde{s}}$
-%	\item[(2)] $\ostate{\tilde{pre(s)}}\in\textit{Explored}\text{-}\{\ostate{\tilde{s}}\}$
-%\end{enumerate}
-%By induction, there must exists a sequence $\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s}}$ where all the $\textit{Pred}_i$ are satisfiable.
-%
-%Then $\forall\ostate{\tilde{t}}\textit{Explored}=State(L)$, there are also two cases:
-%\begin{enumerate}
-%	\item[(1)] $\ostate{\tilde{t}}\in State(L1)$
-%	
-%	By definition of reachability, there exists a sequence $\ostate{\tilde{s_0}}...\xrightarrow{v_j}...\ostate{\tilde{t}}$ where all the $\textit{Pred}_j$ are satisfiable.
-%	
-%	$\Rightarrow \ostate{\tilde{t}}\in State(L_{Smart})$
-%	\item[(2)] $\ostate{\tilde{t}}\in State(L)\text{-}State(L1)$, then $\forall \ostate{\tilde{u}}\in\textit{Explored}-\{\ostate{\tilde{t}}\}$,
-%	\begin{enumerate}
-%		\item[(1)] $\ostate{\tilde{u}}\in State(L)\text{-}State(L1)$.
-%		\item[(2)] $\ostate{\tilde{u}}\in State(L1)$, but there is no transition $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{t}}$.
-%		\item[(3)] $\ostate{\tilde{u}}\in State(L1)$, there exists transition $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{t}}$, but the $\textit{Pred}_u$ is unsatisfiable.
-%	\end{enumerate}
-%	By induction, there is no sequence from $\ostate{\tilde{s_0}}$ to $\ostate{\tilde{t}}$.
-%	
-%	$\Rightarrow \ostate{\tilde{t}}\notin State(L_{Smart})$
-%\end{enumerate}
-%Overall, $State(L1)$ is equal to $State(L_{Smart})$.
 \end{proof}
@@
 
-\TODO{Xudong: proof - to be checked}
-
+\TODO{Formalize the proof}
+
+\ERIC{Proof sketch:}
+
+  \begin{itemize}
+   \item $L1$ = original set of transitions by Algorithm 1, after
+      satisfiability check (i.e. after line 11), using assignments
+      from the whole state space.
+   \item $L2$ = original set of transitions by Algorithm 1, after
+      satisfiability check (i.e. after line 11), using assignments
+      from the original on-the-fly search.
+
+    \item $L1-reach$ = final set of OTs of Algorithm 1, as computed
+        by an iterative application of makeReachableSubAutomaton (line
+        12) up to fixpoint.
+      \item $L2-reach$ = final set of OTs of Algorithm 2, as computed
+          by line 13, as computed
+        by an iterative application of makeReachableSubAutomaton (line
+        16) up to fixpoint.
+  \end{itemize}
+
+  Proof similar to the previous case still apply here, but adapted as
+  we are building a different starting point :
+
+  - Define the function $States$ as before, and  $Assignments : OT^* \# State -> $ the function
+  computing the set of assignments of a global state from a given set of OTs.
+
+  - The structure implicitely computed by the algorithm (comprised in
+  the structure of an Open Automaton) is a triple $ Aut= <States, OTs,
+  Assigns>$.
+
+  - when building $L1$ and $L2$ the 2 algorithms compute the initial
+  $Aut_0$ structures, without using previous assignments, as
+  explained in section~\ref{section:implementation}.
+
+  - The function $Refine : Aut->Aut$, implemented as
+  $makeReachableSubAutomaton(S0,OTs)$, uses the assignments of the
+  previous step to refine the computed reachable space, reducing all 3
+  components of the triple: by pruning some Unsat OTs, it potentialy
+  removes the corresponding assignments, and their target states.
+
+  - the whole computation takes place within a finite domain: Global
+  states are within the cartesian product of the pLTS states; OTs are
+  always subsets of $L1$, and Assignments are a fixed finite set of
+  symbolic assignements of expressions to state variables,
+  syntacticaly contained in the OTs in $L1$; so the fixpoint
+  computation terminates.
+
+  - the result $Aut$ contains all reachable OTs and States from $L1$,
+  and only these (proof should be similar to that of Th2).
+
+  \medskip
+  \noteInEM{I keep below the original proof draft from Xudong, though
+    think it does not apply any more}
 \begin{proof}

### 2019-03-27 2017-Xudong-SMT/ActaInformatica.tex
reorganization 5.4, small bugs, and rewritten conclusion

@@
 
-For this example, the tool (using Algorithm 1) builds 258 open transitions, whereof 248
+For this example, the tool (using Algorithm 1) builds 408 open transitions, whereof 396
 are detected unsatisfiable by Z3.  The resulting open automaton, with
-3 reachable global states (out of the possible 6) and 10 open
+3 reachable global states (out of the possible 6) and 12 open
 transitions, is shown in Figure~\ref{schema:resultOA1}.
@@
 system.
+In this section, we use a combination of 2 FailureTimer architectures
+to demonstrate how the encoding works, and as a slightly larger
+example to show how the approach scales up.
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=0.9\columnwidth]{ActaXFIG/BIPspec-DoubleArchFailureTimer-v2-2}
+  \caption{The BIP specification of two composed Failure Monitor architectures}
+  \label{schema:ArchFailure:BIP:Double}
+\end{figure}
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=0.9\columnwidth]{ActaXFIG/Double-OA}
+  \caption{The resulting automaton}
+  \label{schema:ArchFailure:Double:OA}
+\end{figure}
 
@@
 be synchronous: each can only tick after the other has also started,
-and then they will tick, and timeout, synchronously.
-
-\TODO{Eric: try reorganise the figures. Add properties ?}
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=0.9\columnwidth]{ActaXFIG/BIPspec-DoubleArchFailureTimer-v2-2}
-  \caption{The BIP specification of two composed Failure Monitor architectures}
-  \label{schema:ArchFailure:BIP:Double}
-\end{figure}
-
-\begin{figure}[ht]
-  \centering
-  \includegraphics[width=0.9\columnwidth]{ActaXFIG/Double-OA}
-  \caption{The resulting automaton}
-  \label{schema:ArchFailure:Double:OA}
-\end{figure}
-
-%% \begin{figure}[t]
-%%   \centering
-%%   \includegraphics[width=0.9\columnwidth]{ActaXFIG/DoubleFailureTimerPNET-v2-2}
-%%   \caption{The open pNet encoding the Failure Monitor architecture (\ref{fig:schema:ArchFailure:BIP})}
-%%   \label{fig:FailureTimer:pNet}
-%% \end{figure}
-
-%% \begin{figure}[t]
-%%   \centering
-%%   \includegraphics[width=0.9\columnwidth]{XFIG/DoubleTimerOA-v2-2}
-%%   \caption{The open Automaton of the Failure Monitor Architecture}
-%%   \label{fig:ArchFailure:OA}
-%% \end{figure}
+and then they will tick, reset, and timeout, synchronously.
+
+This is a very strong assumption, and we are working on a more
+flexible specification (at BIP level) to release this hypothesis while
+keeping the safety properties of the composition.
 
@@
 
-All tests are run on HP xxx laptop under Windows 10 x64, with an Intel quad-Core i7-6600U
+All tests are run on HP EliteBook 840 laptop under Windows 10 x64, with an Intel quad-Core i7-6600U
 processor, and 32Gb of RAM. The software platform is VerCors\footnote{Available at \url{https://team.inria.fr/scale/software/vercors/}.}, running on top of
@@
 %
-In this paper, we used a running example, based on a BIP
-architecture from an earlier nanosatellite case
-study~\cite{CubETH-case-study}.  This example shows that
+We have used a running example based on two possible
+encodings of the Enable operator of Lotos. The automata computed with
+the algorithm can be used to prove equational properties of the
+operator.
+
+Then we define a ``smart'' version of the algorithm that explores, as
+much as possible, only the reachable part of the open automaton. The
+handling of assignments makes the reachable computation more
+challenging. We show that the result is equivalent to the original
+algorithm.
+
+We validate the approach on two larger examples, 
+based on a BIP architecture taken from an earlier nanosatellite case
+study~\cite{CubETH-case-study}. We also show how such architectures
+can be composed, and how our approach scales.
+This example shows that
 open-automata-based semantics can be instrumental in verifying the
 properties enforced by the architectures through an encoding into open
-pNets.  This encoding %\mdash which we intend to formalise and prove
-% correct in a separate paper\mdash 
-also opens the way for an extension
-of BIP architectures with the transfer of data among variables of
-different components.  Indeed, such data transfer can be easily
-encoded using the predicates associated to synchronisation vectors in
-open pNets.  The encoding of open transitions into SMTlib and the
-availability of theories can guide the definition of such an extension.
-%
-%}
-%
-Our case-studies show that our encoding
-successfully identifies the unsatisfiable open transitions and that
-the resulting automata correctly reflect the expected 
-movements of the encoded process expressions.
-
-\TODO{add the novelties...}
-
-%% Among the questions that have arised during this work, an important one is the
-%% efficiency of Z3 for our needs. Z3 is famous for being very fast in
-%% solving very large sets of assertions. %% , which could be important for
-%% %% us
-%% However, we encountered problems during the implementation of the
-%% checking method. %% using Z3. 
-%% For example, if the $\mathit{functions}$ and the
-%% $\mathit{datatypes}$ part of the algebra presentation that we submit to the solver
-%% are independent from each other, then checking the $\mathit{assertions}$ is 
-%% simple. However, $\mathit{functions}$ on recursive $\mathit{datatypes}$ make it
-%% more complex. Special rules might be defined by the user for the
-%% induction.  We need more evidence that dealing with more complex
-%% action algebras, which would involve axiomatizing their data structures
-%% as Z3 theories, will allow us to decide validity of
-%% predicates.
-%% We may also try other automatic theorem provers, depending on the structure of the proofs we need.
-
-%% \todoMargin{Change perspective: we are working on the formal extension of
-%%   BIP architectures, and their semantics in terms of pNets. Then
-%%   bisimulation and model-checking principles adapted to open pNet
-%%   systems are under development}
-%
+pNets.
+We also compare the practical performances of the 2 algorithms and
+show the benefit gained using the smart approach.
+
 Naturally, our next goals after the generation of the open automata
-will be to model-check logical properties, and to check equivalences of pNets. While
-model-checking open automata  seems easy to define, equivalence
-checking is more challenging. 
+will be to model-check logical properties, and to check equivalences
+of pNets. While model-checking open automata seems easy to define,
+equivalence checking is more challenging. 
 In~\cite{henrio:Forte2016}, we
-have already found the FH-bisimulation %inspired
-%by~\cite{deSimone85},
-to be a
-suitable definition. But weak equivalences, or refinements, will
+have already found the FH-bisimulation 
+to be a suitable definition. But weak equivalences, or refinements, will
 definitely be useful when comparing different pNets with
-different structures. For bisimulation, we foresee that SMT methods
+different structures. For both model-checking and bisimulation, SMT methods
 will be the basis for comparing open transitions.
-%However, the usual approach of computing bisimulation by partition
-%% refinement does not work easily with symbolic transitions. In a first
-%% step we may want instead to define and implement an algorithm for
-%% checking that a given equivalence relation between open automata 
-%% states is indeed a FH-Bisimulation. Finding automatically a
-%% bisimulation relation or the most general bisimulation will be more
-%% challenging.
-%% It appears also that when comparing different pNets with
-%% different structure, strong bisimulation will be too strong a notion,
-%% and that we will have to define proper notions of weak equivalence or
-%% refinements.
-
-\emph{Scaling up.} One important motivation of this work is to
-attack the complexity of verification of realistic systems by a
-compositional and parametric approach. Still one may wonder if the price
-for analysing our symbolic transitions will not make the approach too expensive
-in terms of computing time. We tried a
-slightly bigger example, assembling two Failure
-controllers. In~\cite{Avocs-RR}, we show that Z3 can check the 
-satisfiablility of  90K open transitions in a couple of minutes.
+
+%% \emph{Scaling up.} One important motivation of this work is to
+%% attack the complexity of verification of realistic systems by a
+%% compositional and parametric approach. Still one may wonder if the price
+%% for analysing our symbolic transitions will not make the approach too expensive
+%% in terms of computing time. We tried a
+%% slightly bigger example, assembling two Failure
+%% controllers. In~\cite{Avocs-RR}, we show that Z3 can check the 
+%% satisfiablility of  90K open transitions in a couple of minutes.
 

### 2019-03-27 2017-Xudong-SMT/ActaInformatica.tex
new proof for Th.2

--- 2019-03-27 2017-Xudong-SMT/ActaInformatica.tex
@@
   \mathit{MkPred}(sv, C, \overline{\mathit{hole}}) = 
-  \\
   (\forall i\in I, a_i=a'_i) \land
@@
 
+%\begin{proof}
+%  Let $pn=<...>$ be a pNet. The set of states 
+%  managed by the two algorithms both are subsets of the cartesian
+%  product of the pLTS states, as defined in \pageref{def-states}. In a
+%  similar way, the set of state variables are also equal. Comparing
+%  transitions requires a little more care, because within the
+%  MakeTransitions function, fresh variables are created everytime a
+%  synchronisation vector is used (this occurs within the $MkPred$ and
+%  $matching$ functions). However, given a global state, the call of
+%  $MakeTransitions$ will always returns exactly the same set of OTs, up to
+%  renaming of these fresh variables\footnote{I think this does not
+%    need any specific proof, given that it is the same function,
+%    called with the same arguments}.
+%
+%  Let us define the following sets of OTs, as computed by the 2
+%  algorithms:
+%  \ERIC{not sure whether all these sets are useful, but it's good to
+%    have them precisely defined for the moment}
+%  \begin{itemize}
+%    \item $L1$ = original set of transitions by Algorithm 1
+%      (i.e. before line 11), 
+%    \item $L1-sat$ = original set of transitions by Algorithm 1, after
+%      satisfiability check (i.e. after line 11),
+%    \item $L1-reach$ = final set of OTs of Algorithm 1, as computed
+%      by line 12.
+%    \item $L2-sat$ = original set of transitions by Algorithm 2
+%      (i.e. before line 13), 
+%    \item $L2-reach$ = final set of OTs of Algorithm 2, as computed
+%          by line 13.
+%  \end{itemize}
+%
+%  For each of these, define $States : OT^* -> State^*$ the function
+%  computing the set of target states of a set of OTs.
+%
+%  We want to prove that $L1-reach = L2-reach$ (upto renaming of fresh
+%  variables) and $States(L1-reach) = States(L2-reach)$.
+%
+%  From the structure of the main loops of the algorithms, we know that
+%  $L1-sat \subset L2-sat$ and subsequently $States(L1-sat) \subset       
+%  States(L2-sat)$.
+%  \qed
+%\end{proof}
+%  
+%    \medskip
+%  \noteInEM{I keep below the original proof draft from Xudong, though
+%    I'm not sure if parts of it can be reused}
 \begin{proof}
-  Let $pn=<...>$ be a pNet. The set of states 
-  managed by the two algorithms both are subsets of the cartesian
-  product of the pLTS states, as defined in \pageref{def-states}. In a
-  similar way, the set of state variables are also equal. Comparing
-  transitions requires a little more care, because within the
-  MakeTransitions function, fresh variables are created everytime a
-  synchronisation vector is used (this occurs within the $MkPred$ and
-  $matching$ functions). However, given a global state, the call of
-  $MakeTransitions$ will always returns exactly the same set of OTs, up to
-  renaming of these fresh variables\footnote{I think this does not
-    need any specific proof, given that it is the same function,
-    called with the same arguments}.
-
-  Let us define the following sets of OTs, as computed by the 2
-  algorithms:
-  \ERIC{not sure whether all these sets are useful, but it's good to
-    have them precisely defined for the moment}
+Let
  \begin{itemize}
@@
       (i.e. before line 11), 
-    \item $L1-sat$ = original set of transitions by Algorithm 1, after
+    \item $L1_{sat}$ = original set of transitions by Algorithm 1, after
       satisfiability check (i.e. after line 11),
-    \item $L1-reach$ = final set of OTs of Algorithm 1, as computed
+    \item $L1_{reach}$ = final set of OTs of Algorithm 1, as computed
       by line 12.
-    \item $L2-sat$ = original set of transitions by Algorithm 2
+    \item $L2_{sat}$ = original set of transitions by Algorithm 2
       (i.e. before line 13), 
-    \item $L2-reach$ = final set of OTs of Algorithm 2, as computed
+    \item $L2_{reach}$ = final set of OTs of Algorithm 2, as computed
           by line 13.
 \end{itemize}
-
-  For each of these, define $States : OT^* -> State^*$ the function
-  computing the set of target states of a set of OTs.
-
-  We want to prove that $L1-reach = L2-reach$ (upto renaming of fresh
-  variables) and $States(L1-reach) = States(L2-reach)$.
-
-  From the structure of the main loops of the algorithms, we know that
-  $L1-sat \subset L2-sat$ and subsequently $States(L1-sat) \subset       
-  States(L2-sat)$.
-  \qed
-\end{proof}
-
-    \medskip
-  \noteInEM{I keep below the original proof draft from Xudong, though
-    I'm not sure if parts of it can be reused}
-\begin{proof}
-%% Let $L$, $L1$, $L_{Smart}$ respectively mean the result open transition set of original algorithm before pruning, original algorithm after pruning and smart algorithm.
-Similarly, $State(L)$, $State(L1)$, $State(L_{Smart})$ mean the result global state set of them.
-According to the algorithm, there has $L_{Smart}\in L$ and $State(L_{Smart})\in State(L)$.
-
-We will construct a mapping $f$: $State(L1-reach)\rightarrow
-State(L2-reach)$.
-\ERIC{I do not understand this, as states are identical. You would
-  rather need mapping betwen transitions ?}
-\begin{enumerate}
-\setlength{\itemindent}{3.5em}
-	\item[(Surjective)] If $\ostate{\tilde{s_0}}=Initial(p)$ then $f(\ostate{\tilde{s}})=\ostate{\tilde{t_0}}=Initial(p)$ must exists, the transitions started from them fulfill that
-	\[\forall \ostate{\tilde{t_0'}}, \ostate{\tilde{t_0}}\xrightarrow{v_j}\ostate{\tilde{t_0'}}\in L_{Smart},\quad \exists\ostate{\tilde{s'}},\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}\in L.\]
-	The state $\ostate{\tilde{t'}}\in State(L_{Smart})$ and as $Pred_j$ of $\ostate{\tilde{t}}\xrightarrow{v_j}\ostate{\tilde{t_0'}}$ is satisfiable, then if the $Pred_i$ of $\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}$ is also satisfiable, the state $\ostate{\tilde{s_0'}}$ is reachable in the original open automaton s.t.
+When the pNets contains no assignment, there is no need for the last filtering step, so $L1_{sat}=L1_{reach}$ and $L2_{sat}=L2_{reach}$.
+
+For each of these, define $States: <OT> \rightarrow <State>$ which is the function computing the set of states in a set of OTs. Between two transitions sets of the
+algorithms, define $Rename:  L1_{reach} \rightarrow L2_{reach}$ which is the function renaming fresh variables.
+
+According to the rules Tr1 and Tr2 in \pageref{def-states}, the global state $\ostate{\tilde{s}}=\ostate{\tilde{s_0...s_n}}$ is a composition of n pLTS states $s_{i}^{i\in [0,n]}$.
+
+From the structure of the main loop of the algorithms, we can get $States(L2_{reach})\subseteq  States(L1)$, then
+\[\forall \ostate{\tilde{u}}\in States(L2_{reach}), \exists\ostate{\tilde{t}}\in States(L1), \ostate{\tilde{t}}=\ostate{\tilde{a_0...a_n}}=\ostate{\tilde{u}}.\]
+
+Suppose that  $\ostate{\tilde{t}}\in States(L1_{reach})$, it is reachable in the result automaton of Algorithm 1, so there exists a sequence of transitions $\ostate{\tilde{t_0}}...\xrightarrow{v_i}...\ostate{\tilde{t}}$ where $Pred_i$ are all satisfiable.
+And there exists $\ostate{\tilde{u}}\in States(L2_{reach})$ where $\ostate{\tilde{t}}=\ostate{\tilde{u}}$.
+
+Similarly, from the structure of the algorithms, 
+\[\forall \ostate{\tilde{u}}\in States(L2_{reach}), \exists\ostate{\tilde{t}}\in States(L1), \ostate{\tilde{t}}=\ostate{\tilde{u}}\]
+\[s.t.\quad OT_t = \ostate{\tilde{t}}\xrightarrow{v}\ostate{\tilde{t'}}\in L1, OT_u = \ostate{\tilde{u}}\xrightarrow{v}\ostate{\tilde{u'}}\in L2_{reach}, Rename(OT_t) = OT_u.\]
+where $Pred_t$ and $Pred_u$ are satisfiable.
+
+Then we can get a new longer sequence $\ostate{\tilde{t_0}}...\xrightarrow{v_i}...\ostate{\tilde{t'}}$ implying that $\ostate{\tilde{t'}}\in States(L1_{reach}),OT_t\in L1_{reach}$. So 
+$States(L2_{reach})\subseteq  States(L1_{reach})$.
+
+Moreover,
+\[\forall OT_u\notin L2_{reach}, \exists OT_t\in L1, Rename(OT_t) = OT_u\]
+where $Pred_t$ and $Pred_u$ are not satisfiable. Then according to the pruning function in Algorithm 1, $OT_t\notin L1_{reach}$.
+
+As a result, we get that $L1_{reach}=L2_{reach}$, and subsequently, $States(L1_{reach})=States(L2_{reach})$.
+%We will construct a mapping $f$: $State(L1-reach)\rightarrow
+%State(L2-reach)$.
+%\ERIC{I do not understand this, as states are identical. You would
+%  rather need mapping betwen transitions ?}
+%\begin{enumerate}
+%\setlength{\itemindent}{3.5em}
+%	\item[(Surjective)] If $\ostate{\tilde{s_0}}=Initial(p)$ then $f(\ostate{\tilde{s}})=\ostate{\tilde{t_0}}=Initial(p)$ must exists, the transitions started from them fulfill that
+%	\[\forall \ostate{\tilde{t_0'}}, \ostate{\tilde{t_0}}\xrightarrow{v_j}\ostate{\tilde{t_0'}}\in L_{Smart},\quad \exists\ostate{\tilde{s'}},\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}\in L.\]
+%	The state $\ostate{\tilde{t'}}\in State(L_{Smart})$ and as $Pred_j$ of $\ostate{\tilde{t}}\xrightarrow{v_j}\ostate{\tilde{t_0'}}$ is satisfiable, then if the $Pred_i$ of $\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}$ is also satisfiable, the state $\ostate{\tilde{s_0'}}$ is reachable in the original open automaton s.t.
 $\ostate{\tilde{s_0'}}\in State(L1)$, we can construct the mapping
-	\[f(\ostate{\tilde{s_0'}})=\ostate{\tilde{t_0'}}.\]
-	If the $Pred_i$ of $\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}$ is not satisfiable then two transitions are not matched and $\ostate{\tilde{s_0'}}\notin State(L1)$.
-
-	Let $\textit{Explored}$, $\textit{Explored}_{Smart}$ respectively mean the explored states set of original algorithm and smart algorithm.
-
-	Suppose that  $\ostate{\tilde{s}}\in \textit{Explored}$ there is $\ostate{\tilde{t}}\in \textit{Explored}_{Smart}$ where $f(\ostate{\tilde{s}})=\ostate{\tilde{t}}$, there exists a sequence of transitions $\ostate{\tilde{s_0}}...\xrightarrow{v_i}...\ostate{\tilde{s}}$ and $\ostate{\tilde{t_0}}...\xrightarrow{v_j}...\ostate{\tilde{t}}$.
-
-	The transitions $\ostate{\tilde{s}}\xrightarrow{v}\ostate{\tilde{s'}}$ and $\ostate{\tilde{t}}\xrightarrow{v}\ostate{\tilde{t'}}$ have several cases:
-	\begin{enumerate}
-		\item[(1)] $\ostate{\tilde{t'}}\in \textit{Explored}_{Smart}$
-
-		We can find that 
-		 \[\exists\ostate{\tilde{s'}}\in \textit{Explored},\quad \ostate{\tilde{s}}\xrightarrow{v}\ostate{\tilde{s'}}\quad where\quad f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}.\]
-		\item[(2)] $\ostate{\tilde{t'}}\notin \textit{Explored}_{Smart}$
-
-		There must has 
-		\[\exists\ostate{\tilde{s'}}\notin \textit{Explored},\quad \ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}.\]
-		If the $Pred_i$ of $\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$ is satisfiable then there exists a sequence of transitions $\ostate{\tilde{s_0}}...\xrightarrow{v_i}...\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$.
+%	\[f(\ostate{\tilde{s_0'}})=\ostate{\tilde{t_0'}}.\]
+%	If the $Pred_i$ of $\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}$ is not satisfiable then two transitions are not matched and $\ostate{\tilde{s_0'}}\notin State(L1)$.
+%	
+%	Let $\textit{Explored}$, $\textit{Explored}_{Smart}$ respectively mean the explored states set of original algorithm and smart algorithm.
+%	
+%	Suppose that  $\ostate{\tilde{s}}\in \textit{Explored}$ there is $\ostate{\tilde{t}}\in \textit{Explored}_{Smart}$ where $f(\ostate{\tilde{s}})=\ostate{\tilde{t}}$, there exists a sequence of transitions $\ostate{\tilde{s_0}}...\xrightarrow{v_i}...\ostate{\tilde{s}}$ and $\ostate{\tilde{t_0}}...\xrightarrow{v_j}...\ostate{\tilde{t}}$.
+%	
+%	The transitions $\ostate{\tilde{s}}\xrightarrow{v}\ostate{\tilde{s'}}$ and $\ostate{\tilde{t}}\xrightarrow{v}\ostate{\tilde{t'}}$ have several cases:
+%	\begin{enumerate}
+%		\item[(1)] $\ostate{\tilde{t'}}\in \textit{Explored}_{Smart}$
+%		
+%		We can find that 
+%		 \[\exists\ostate{\tilde{s'}}\in \textit{Explored},\quad \ostate{\tilde{s}}\xrightarrow{v}\ostate{\tilde{s'}}\quad where\quad f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}.\]
+%		\item[(2)] $\ostate{\tilde{t'}}\notin \textit{Explored}_{Smart}$
+%		
+%		There must has 
+%		\[\exists\ostate{\tilde{s'}}\notin \textit{Explored},\quad \ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}.\]
+%		If the $Pred_i$ of $\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$ is satisfiable then there exists a sequence of transitions $\ostate{\tilde{s_0}}...\xrightarrow{v_i}...\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$.
 So the $\ostate{\tilde{s'}}$ is reachable in the original open automaton, we can construct the mapping
-		\[f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}.\]
-		If the $Pred_i$ of $\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$ is not satisfiable then two transitions are not matched and $\ostate{\tilde{s'}}\notin State(L1)$.
-	\end{enumerate}	
-	Overall, \[\forall \ostate{\tilde{t}}\in State(L_{Smart}),\quad \exists\ostate{\tilde{s}}\in State(L1), f(\ostate{\tilde{s}})=\ostate{\tilde{t}}.\]
-	\item[(Injective)] If there is a pair of states $\ostate{\tilde{s}} and \ostate{\tilde{t}}$ constructs the mapping $f(\ostate{\tilde{s}})=\ostate{\tilde{t}}$.
+%		\[f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}.\]
+%		If the $Pred_i$ of $\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$ is not satisfiable then two transitions are not matched and $\ostate{\tilde{s'}}\notin State(L1)$.
+%	\end{enumerate}	
+%	Overall, \[\forall \ostate{\tilde{t}}\in State(L_{Smart}),\quad \exists\ostate{\tilde{s}}\in State(L1), f(\ostate{\tilde{s}})=\ostate{\tilde{t}}.\]
+%	\item[(Injective)] If there is a pair of states $\ostate{\tilde{s}} and \ostate{\tilde{t}}$ constructs the mapping $f(\ostate{\tilde{s}})=\ostate{\tilde{t}}$.
 We can know that $\ostate{\tilde{s}}\in \textit{Explored},\ostate{\tilde{t}}\in \textit{Explored}_{Smart}$.
-
-	As when there is $\ostate{\tilde{t'}}\in \textit{Explored}_{Smart}$, the state is must be $\ostate{\tilde{s'}}\in \textit{Explored}$ where $f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}$.
-	So it is a one-to-one mapping.
-\end{enumerate}
-
-Then as the function $f$ is both surjective and injective, it is a bijective function. The theorem is proved.
-
+%	
+%	As when there is $\ostate{\tilde{t'}}\in \textit{Explored}_{Smart}$, the state is must be $\ostate{\tilde{s'}}\in \textit{Explored}$ where $f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}$.
+%	So it is a one-to-one mapping.
+%\end{enumerate}
+%
+%Then as the function $f$ is both surjective and injective, it is a bijective function. The theorem is proved.
+%
 \end{proof}

### 2019-03-28 2017-Xudong-SMT/ActaInformatica.tex
Refine the proof of Th.2 after the discussion with Prof.Min.

@@
 
-Suppose that  $\ostate{\tilde{t}}\in States(L1_{reach})$, it is reachable in the result automaton of Algorithm 1, so there exists a sequence of transitions $\ostate{\tilde{t_0}}...\xrightarrow{v_i}...\ostate{\tilde{t}}$ where $Pred_i$ are all satisfiable.
-And there exists $\ostate{\tilde{u}}\in States(L2_{reach})$ where $\ostate{\tilde{t}}=\ostate{\tilde{u}}$.
-
-Similarly, from the structure of the algorithms, 
-\[\forall \ostate{\tilde{u}}\in States(L2_{reach}), \exists\ostate{\tilde{t}}\in States(L1), \ostate{\tilde{t}}=\ostate{\tilde{u}}\]
-\[s.t.\quad OT_t = \ostate{\tilde{t}}\xrightarrow{v}\ostate{\tilde{t'}}\in L1, OT_u = \ostate{\tilde{u}}\xrightarrow{v}\ostate{\tilde{u'}}\in L2_{reach}, Rename(OT_t) = OT_u.\]
-where $Pred_t$ and $Pred_u$ are satisfiable.
-
-Then we can get a new longer sequence $\ostate{\tilde{t_0}}...\xrightarrow{v_i}...\ostate{\tilde{t'}}$ implying that $\ostate{\tilde{t'}}\in States(L1_{reach}),OT_t\in L1_{reach}$. So 
-$States(L2_{reach})\subseteq  States(L1_{reach})$.
+If there is an initial state $\ostate{\tilde{t_0}}\in States(L2_{reach})$ then the initial state of the original automaton $\ostate{\tilde{t_0}}\in States(L1_{reach})$ must exists.
+
+Suppose that  $\ostate{\tilde{t}}\in States(L2_{reach})$, it is reachable in the result automaton of Algorithm 2, so there exists a sequence of transitions $\ostate{\tilde{t_0}}...\xrightarrow{v_j}...\ostate{\tilde{t}}$ where $Pred_j$ are all satisfiable.
+Then there exists the same state $\ostate{\tilde{t}}\in States(L1_{reach})$ and $\ostate{\tilde{t_0}}...\xrightarrow{v_i}...\ostate{\tilde{t}}$ where $Pred_i$ are all satisfiable.
+From the structure of the algorithms, 
+\[\forall \ostate{\tilde{t}}\in States(L2_{reach}), OT = \ostate{\tilde{t}}\xrightarrow{v}\ostate{\tilde{t'}}\in L2_{reach}\]
+\[\exists OT' = \ostate{\tilde{t}}\xrightarrow{v'}\ostate{\tilde{t'}}\in L1 \quad s.t.\quad Rename(OT') = OT.\]
+where $Pred$ and $Pred'$ are satisfiable.
+
+Then we can get a new longer sequence $\ostate{\tilde{t_0}}...\xrightarrow{v_i}...\ostate{\tilde{t'}}\xrightarrow{v'}\ostate{\tilde{t'}}$ implying that $\ostate{\tilde{t'}}\in States(L1_{reach}),OT'\in L1_{reach}$.
+So
+$L2_{reach}\subseteq  L1_{reach}$.
 
 Moreover,
-\[\forall OT_u\notin L2_{reach}, \exists OT_t\in L1, Rename(OT_t) = OT_u\]
-where $Pred_t$ and $Pred_u$ are not satisfiable. Then according to the pruning function in Algorithm 1, $OT_t\notin L1_{reach}$.
+\[\forall OT\notin L2_{reach}, \exists OT'\in L1, Rename(OT') = OT\]
+where $Pred$ and $Pred'$ are not satisfiable. Then according to the pruning function in Algorithm 1, $OT'\notin L1_{reach}$.
 

### 2019-03-28 2017-Xudong-SMT/ActaInformatica.tex
New proof for Th.3 after discussion with Prof.Zhang.

@@
 
-For each of these, define $States: <OT> \rightarrow <State>$ which is the function computing the set of states in a set of OTs. Between two transitions sets of the
+For each of these, define $States: \langle OT\rangle\rightarrow\langle State\rangle$ which is the function computing the set of states in a set of OTs. Between two transitions sets of the
 algorithms, define $Rename:  L1_{reach} \rightarrow L2_{reach}$ which is the function renaming fresh variables.
@@
   \label{Th:CorrectnessWithAssignments}
-In the general case, the smart algorithm computes 
+In the general case, if a pNet contains some assignments to state variables, the smart algorithm computes 
 the same open automaton as that of Algorithm 1 up to a renaming of variables in the transition labels.
@@
 \TODO{Formalize the proof}
+\begin{proof}
+In Theorem 2, we have already proved the result automaton $OA_1$ and $OA_2$ of two algorithm are the same without the assignments.
+
+Define the function $States$ as before, and  $Assignments : \langle OT\rangle\times\langle State\rangle\rightarrow\langle Assign\rangle$ the function
+computing the set of assignments of a global state from a given set of OTs.
+
+The structure implicitely computed by the algorithm (comprised in
+the structure of an Open Automaton) is a triple $ Aut= \langle OTs, States, Assigns\rangle$.
+
+Then the assignments set of $OA_1$ is $Assignments(L1, States(L1))$ and $OA_2$ is $Assignments(L2_{reach}, States(L2_{reach}))$. The computed triples are 
+\[Aut_1 = \langle L1_{reach}, States(L1_{reach}), Assignments(L1, States(L1))\rangle\] and \[Aut_2 = \langle L2_{reach}, States(L2_{reach}), Assignments(L2_{reach}, States(L2_{reach}))\rangle\]
+
+Based on the notation of the triple, define the function $Refine : Aut \rightarrow Aut$ refining the result automaton together with the assignments,
+\begin{align*}
+Refine(Aut) &=\langle OT', States(OT'), Assignments(OT', States(OT'))\rangle \\
+&=Aut'
+\end{align*}
+where $OT' = OT - OT_{unsat}$, $OT_{unsat}$ is the set of transitions checked unsatisfiable in this iteration.
+
+Given that every iteration will remove some unsatisfiable transitions, $Refine$ is a monotone function. There exists a sequence $Aut^n = Refine(Aut^{n-1})$ s.t. $|Aut^n|\le |Aut^{n-1}|$.
+Let $Aut''$ contains the $OT''$ which has no more unsatisfiable transition, then there is $Aut'' = Refine(Aut'')$ and $|Aut''| = |Refine(Aut'')|$.
+
+Let the fixed point of $OA_1$ to be $Aut''_1$ and the fixed point of $OA_2$ to be $Aut''_2$.
+
+For the transitions set in $Aut''_1$ and $Aut''_2$, $L1_{reach}''$ and $L2''_{reach}$, we need to check their equivalence.
+At the first iteration, the unsatisfiable transitions in $OA_1$ has only one case.
+\begin{align*}
+&\quad Pred\and \bigwedge_i Assignments_i(L1, States(L1) \text{ is false}\\
+&\quad\rightarrow Pred \and \bigwedge_j Assignments_j(L2_{reach}, States(L2_{reach})\text{ is false}\\
+&\Rightarrow \forall t\in L1_{unsat} \rightarrow t\in L2_{unsat}\\
+&\Rightarrow L1_{unsat}\subseteq L2_{unsat}.
+\end{align*}
+However, its reverse direction is not fulfilled. Recall that $L1_{reach}=L2_{reach}$, these relation can imply that,
+\begin{align*}
+Assignments(L1, &States(L1)\supseteq Assignments(L2_{reach}, States(L2_{reach})\\
+&\supseteq Assignments(L1_{reach}-L1_{unsat}, States(L1_{reach}-L1_{unsat}))\\
+&\supseteq Assignments(L2_{reach}-L2_{unsat}, States(L2_{reach}-L2_{unsat}))
+\end{align*}
+So after the first iteration, the unsatisfiable transitions in $OA_1$ has two cases.
+\begin{align*}
+&\forall t\in L1'_{unsat} \rightarrow t\in L2'_{unsat}\\
+\text{ or }&\forall t\in L1'_{unsat} \rightarrow t\notin L2'_{reach}.
+\end{align*}
+By induction, after removing all the transitions not in the $L2''_{reach}$, we can get that $L1''_{reach}=L2''_{reach}$, subsequently, $States(L1''_{reach})=States(L2''_{reach})$,
+$Assignments\\(L1''_{reach},States''_{L1_{reach}})=Assignments(L2''_{reach},States''_{L2_{reach}})$.
+\end{proof}
 
@@
     think it does not apply any more}
-\begin{proof}
-In Theorem 2, we have already proved the result set of global states of two algorithm are the same without the assignments.
-
-If there exists assignments in the open transitions.
-
-In Algorithm 3, $\forall\ostate{\tilde{t}}\notin State(L_{Smart})$, if there is a transition $\ostate{\tilde{t}}\xrightarrow{v_t}\ostate{\tilde{t'}}$ contains an assignment $\textit{Post}_t$, and in following transitions $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{u'}}$, we need to check $\textit{Pred}\and\bigwedge\textit{Post}_i$ where $\textit{Post}_i \notin \{\textit{Post}_t\}$.
-
-In Algorithm 1, the same state $\ostate{\tilde{t}}\notin State(L1)$, also has a transition $\ostate{\tilde{t}}\xrightarrow{v_t}\ostate{\tilde{t'}}$ contains an assignment $\textit{Post}_t$, and in following transitions $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{u'}}$, what need to check is $\textit{Pred}\and\bigwedge\textit{Post}_i$.
-As $b_1\and b_2\rightarrow b_1$, if $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{u'}}$ exists in the result of Algorithm 3, it is also contained in the original result.
-
-After the final reachability computation, $\{\textit{Post}_t\}$ is removed from $\{\textit{Post}_i\}$ then the assertions to check become the same, then the transitions of the result are also the same.
-So the result open automaton of Algorithm 3 is exactly the same as that of  Algorithm 1.
-\end{proof}
 

### 2019-03-28 2017-Xudong-SMT/ActaInformatica.tex
Correct some typing error and wrong notation applying.
Lx_{reach} in Th.3 should be Lx_{sat}.

@@
 
-Then the assignments set of $OA_1$ is $Assignments(L1, States(L1))$ and $OA_2$ is $Assignments(L2_{reach}, States(L2_{reach}))$. The computed triples are 
-\[Aut_1 = \langle L1_{reach}, States(L1_{reach}), Assignments(L1, States(L1))\rangle\] and \[Aut_2 = \langle L2_{reach}, States(L2_{reach}), Assignments(L2_{reach}, States(L2_{reach}))\rangle\]
+Then the assignments set of $OA_1$ is $Assignments(L1, States(L1))$ and $OA_2$ is $Assignments(L2_{sat}, States(L2_{sat}))$. The computed triples are 
+\[Aut_1 = \langle L1_{sat}, States(L1_{sat}), Assignments(L1, States(L1))\rangle\] and \[Aut_2 = \langle L2_{sat}, States(L2_{sat}), Assignments(L2_{sat}, States(L2_{sat}))\rangle\]
 
@@
 
-Let the fixed point of $OA_1$ to be $Aut''_1$ and the fixed point of $OA_2$ to be $Aut''_2$.
-
-For the transitions set in $Aut''_1$ and $Aut''_2$, $L1_{reach}''$ and $L2''_{reach}$, we need to check their equivalence.
-At the first iteration, the unsatisfiable transitions in $OA_1$ has only one case.
+Let the fixed points $Refine(Aut''_1) = Aut''_1$, $Refine(Aut''_2) = Aut''_2$.
+
+For the transitions set in $Aut''_1$ and $Aut''_2$, $L1''_{sat}=L1_{reach}$ and $L2''_{sat}=L2_{reach}$, we need to check their equivalence.
+At the first iteration, the unsatisfiable transitions in $OA_1$ has only one case according to the relation between the assertions to check,
 \begin{align*}
-&\quad Pred\and \bigwedge_i Assignments_i(L1, States(L1) \text{ is false}\\
-&\quad\rightarrow Pred \and \bigwedge_j Assignments_j(L2_{reach}, States(L2_{reach})\text{ is false}\\
-&\Rightarrow \forall t\in L1_{unsat} \rightarrow t\in L2_{unsat}\\
+&\quad Pred\wedge \bigvee_i Assignments_i(L1, States(L1) \text{ is false}\\
+&\quad\longrightarrow Pred\wedge \bigvee_j Assignments_j(L2_{sat}, States(L2_{sat})\text{ is false}\\
+&\Rightarrow \forall t\in L1_{unsat} \longrightarrow t\in L2_{unsat}\\
 &\Rightarrow L1_{unsat}\subseteq L2_{unsat}.
 \end{align*}
-However, its reverse direction is not fulfilled. Recall that $L1_{reach}=L2_{reach}$, these relation can imply that,
+However, its reverse direction is not fulfilled. Recall that $L1_{sat}=L2_{sat}$, these relations can imply that,
 \begin{align*}
-Assignments(L1, &States(L1)\supseteq Assignments(L2_{reach}, States(L2_{reach})\\
-&\supseteq Assignments(L1_{reach}-L1_{unsat}, States(L1_{reach}-L1_{unsat}))\\
-&\supseteq Assignments(L2_{reach}-L2_{unsat}, States(L2_{reach}-L2_{unsat}))
+Assignments(L1, &States(L1))\supseteq Assignments(L2_{sat}, States(L2_{sat}))\\
+&\supseteq Assignments(L1_{sat}-L1_{unsat}, States(L1_{sat}-L1_{unsat}))\\
+&\supseteq Assignments(L2_{sat}-L2_{unsat}, States(L2_{sat}-L2_{unsat}))
 \end{align*}
-So after the first iteration, the unsatisfiable transitions in $OA_1$ has two cases.
+So after the first iteration, the unsatisfiable transitions in $OA_1$ has two cases,
 \begin{align*}
-&\forall t\in L1'_{unsat} \rightarrow t\in L2'_{unsat}\\
-\text{ or }&\forall t\in L1'_{unsat} \rightarrow t\notin L2'_{reach}.
+&\forall t\in L1'_{unsat} \longrightarrow t\in L2'_{unsat}\\
+\text{ or }&\forall t\in L1'_{unsat} \longrightarrow t\notin L2'_{sat}.
 \end{align*}
-By induction, after removing all the transitions not in the $L2''_{reach}$, we can get that $L1''_{reach}=L2''_{reach}$, subsequently, $States(L1''_{reach})=States(L2''_{reach})$,
-$Assignments\\(L1''_{reach},States''_{L1_{reach}})=Assignments(L2''_{reach},States''_{L2_{reach}})$.
+By induction, after removing all the transitions not in the $L2''_{sat}$, we can get that $L1_{reach}=L2_{reach}$, subsequently, $States_{L1_{reach}}=States_{L2_{reach}}$,
+$Assignments\\(L1_{reach},States_{L1_{reach}})=Assignments(L2_{reach},States_{L2_{reach}})$.
 \end{proof}

### 2019-03-28 2017-Xudong-SMT/ActaInformatica.tex
small edition to the beginning of proof 2

@@
   \label{Th:CorrectnessWithoutAssignments}
-If a pNet contains no assignment to state variables, then the smart
+If a pNet verifying the finiteness conditions of theorem 1, and
+containing no assignment to state variables, then the smart  
 algorithm, without a final reachability computation, computes 
@@
 %    I'm not sure if parts of it can be reused}
-\begin{proof}
+\begin{proof of Theorem \ref{Th:CorrectnessWithoutAssignments}}
+
 Let
@@
 \end{itemize}
-When the pNets contains no assignment, there is no need for the last filtering step, so $L1_{sat}=L1_{reach}$ and $L2_{sat}=L2_{reach}$.
-
-For each of these, define $States: \langle OT\rangle\rightarrow\langle State\rangle$ which is the function computing the set of states in a set of OTs. Between two transitions sets of the
-algorithms, define $Rename:  L1_{reach} \rightarrow L2_{reach}$ which is the function renaming fresh variables.
-
-According to the rules Tr1 and Tr2 in \pageref{def-states}, the global state $\ostate{\tilde{s}}=\ostate{\tilde{s_0...s_n}}$ is a composition of n pLTS states $s_{i}^{i\in [0,n]}$.
+
+For each of these, define $States: \langle OT\rangle\rightarrow\langle
+State\rangle$ which is the function computing the set of states in a
+set of OTs. Between two transitions sets of the algorithms, define
+$Rename:  L1_{reach} \rightarrow L2_{reach}$ which is the function
+renaming fresh variables.
+
+When the pNets contains no assignment, there is no need for the last
+filtering step, so $L1_{sat}=L1_{reach}$ and $L2_{sat}=L2_{reach}$.
+
+According to the definition of global states in
+page~\pageref{def-states}, the global state
+$\ostate{\tilde{s}}=\ostate{\tilde{s_0...s_n}}$ is a composition of n
+pLTS states $s_{i}^{i\in [0,n]}$.
 
@@
 \[\forall \ostate{\tilde{u}}\in States(L2_{reach}), \exists\ostate{\tilde{t}}\in States(L1), \ostate{\tilde{t}}=\ostate{\tilde{a_0...a_n}}=\ostate{\tilde{u}}.\]
-
-If there is an initial state $\ostate{\tilde{t_0}}\in States(L2_{reach})$ then the initial state of the original automaton $\ostate{\tilde{t_0}}\in States(L1_{reach})$ must exists.
+\noteInEric{I don't agree with the previous statement: the main loop
+  constructs L1 (resp $L2_{sat}$), note the sets of states, so this
+  argument would give you
+
+The reachability function $computeReachableSubAutomaton$ being called
+with the same initial state $\ostate{\tilde{t_0}}$, this state is the
+initial state of both $L1_{reach})$ and $L2_{reach})$.
+
+%  If there is an initial state $\ostate{\tilde{t_0}}\in States(L2_{reach})$ then the initial state of the original automaton $\ostate{\tilde{t_0}}\in States(L1_{reach})$ must exists.
+
+\noteInEM{What you are doing below is a proof by recursion on the
+  length of the path reaching a given OT, isn't it ? I suggest you
+  explicite this and conclude $L2_{reach}\subseteq  L1_{reach}$.}
 
@@
 
-Moreover,
+%Moreover,
+Conversely,
 \[\forall OT\notin L2_{reach}, \exists OT'\in L1, Rename(OT') = OT\]

### 2019-03-29 2017-Xudong-SMT/ActaInformatica.tex
polishing

@@
 	classical process-algebra operator for which we provide several
-	encodings, and prove some basic properties. The second is  industry-oriented and based on the so-called ``BIP architectures'', which have
+	encodings, and prove some basic properties. The second one is  industry-oriented and based on the so-called ``BIP architectures'', which have
 	been used to specify the
@@
 
-\ERIC{The set $L1$ may contain unreachable transitions, the last step of the
-algorithm builds the final Open Automaton as a traversal of $L1$,
+\ERIC{The set $L1$ may contain unreachable transitions. To remove those transitions, the last step of the
+algorithm builds the final open automaton via a traversal of $L1$,
 starting at the initial state $InitState(p)$ as defined in
 page~\pageref{def-states}. More precisely, this is a residual
-algorithm building a graph from transitions in $L1$, and states are
-the set of target states of transitions in $L1$, plus the initial
-states. Each state in the graph is decorated with a set of its local
+algorithm building a graph from the reachable transitions in $L1$. 
+%and states are the set of target states of the transitions. 
+Each state in the graph is decorated with a set of its local
 variables, and a list of their possible assignments,
@@
 checking satisfiability of transitions leaving a given state may
-result in more Unsat transitions: the set of possible
+result in more Unsat transitions. The set of possible
 assignments computed by the algorithm is an over approximation of
@@
 approximation, and potentially more information, which can be used in
-the SAT checking of subsequent transitions. In turn this may reduce the possible
-assignments of the corresponding target states. In theory we should
+the SAT checking of subsequent transitions. In turn, this may reduce the possible
+assignments of the corresponding target states. In theory, we should
 iterate this procedure, each iteration reducing the set of
-transitions, and the sets of assignments; the final Open Automaton
-would be the fix point of this iteration. In practice this would be
+transitions and the sets of assignments; the final open automaton
+would be the fixed point of this iteration. In practice, this would be
 expensive, and it is not incorrect to leave some Unsat OTs in the
-result; in practical cases, very little will be gained computing the
-fixpoint, so we only perform one step. Further algorithms 
+result. From a  practical point of view, very little will be gained to compute the
+fixed point, so we only perform one step of iteration. Further algorithms 
 (e.g. model-checking or equivalence checking) will be able to use the
@@
 
-%\begin{proof}
+\begin{proof}
 %  Let $pn=<...>$ be a pNet. The set of states 
@@
 
-Let
+Let us first define some notations.
  \begin{itemize}
-    \item $L1$ = original set of transitions by Algorithm 1
+    \item $L1$: the original set of transitions by Algorithm 1
       (i.e. before line 11), 
-    \item $L1_{sat}$ = original set of transitions by Algorithm 1, after
+    \item $L1_{sat}$:  the original set of transitions by Algorithm 1, after
       satisfiability check (i.e. after line 11),
-    \item $L1_{reach}$ = final set of OTs of Algorithm 1, as computed
+    \item $L1_{reach}$: the final set of OTs of Algorithm 1, as computed
       by line 12.
-    \item $L2_{sat}$ = original set of transitions by Algorithm 2
+    \item $L2_{sat}$: the original set of transitions by Algorithm 3
       (i.e. before line 13), 
-    \item $L2_{reach}$ = final set of OTs of Algorithm 2, as computed
+    \item $L2_{reach}$: the final set of OTs of Algorithm 2, as computed
           by line 13.
@@
 State\rangle$ which is the function computing the set of states in a
-set of OTs. Between two transitions sets of the algorithms, define
+set of OTs. Between two transition sets of the algorithms, define
 $Rename:  L1_{reach} \rightarrow L2_{reach}$ which is the function
@@
 page~\pageref{def-states}, the global state
-$\ostate{\tilde{s}}=\ostate{\tilde{s_0...s_n}}$ is a composition of n
-pLTS states $s_{i}^{i\in [0,n]}$.
+$\ostate{\tilde{s}}=\ostate{\tilde{s_0...s_n}}$ is a composition of $n$
+PLTS states $s_{i}^{i\in [0,n]}$.
 
@@
 
-  Suppose that  $\ostate{\tilde{t}}\in States(L2_{reach})$, it is reachable in the result automaton of Algorithm 2, so there exists a sequence of transitions $\ostate{\tilde{t_0}}...\xrightarrow{v_j}...\ostate{\tilde{t}}$ where $Pred_j$ are all satisfiable.
+  Suppose that  $\ostate{\tilde{t}}\in States(L2_{reach})$.
+It is reachable in the result automaton of Algorithm 3, so there exists a sequence of transitions $\ostate{\tilde{t_0}}...\xrightarrow{v_j}...\ostate{\tilde{t}}$ where $Pred_j$ are all satisfiable.
 Then there exists the same state $\ostate{\tilde{t}}\in States(L1_{reach})$ and $\ostate{\tilde{t_0}}...\xrightarrow{v_i}...\ostate{\tilde{t}}$ where $Pred_i$ are all satisfiable.
@@
 where $Pred$ and $Pred'$ are not satisfiable. Then according to the pruning function in Algorithm 1, $OT'\notin L1_{reach}$. 
-
 As a result, we get that $L1_{reach}=L2_{reach}$, and subsequently, $States(L1_{reach})=States(L2_{reach})$.
@@
 %
+\hfill\qed
 \end{proof}
@@
 \begin{proof}
-In Theorem 2, we have already proved the result automaton $OA_1$ and $OA_2$ of two algorithm are the same without the assignments.
+In Theorem 2, we have already proved the result automata $OA_1$ and $OA_2$ of the two algorithm are the same without the assignments.
 
@@
 
-The structure implicitely computed by the algorithm (comprised in
-the structure of an Open Automaton) is a triple $ Aut= \langle OTs, States, Assigns\rangle$.
-
-Then the assignments set of $OA_1$ is $Assignments(L1, States(L1))$ and $OA_2$ is $Assignments(L2_{sat}, States(L2_{sat}))$. The computed triples are 
-\[Aut_1 = \langle L1_{sat}, States(L1_{sat}), Assignments(L1, States(L1))\rangle\] and \[Aut_2 = \langle L2_{sat}, States(L2_{sat}), Assignments(L2_{sat}, States(L2_{sat}))\rangle\]
-
-Based on the notation of the triple, define the function $Refine : Aut \rightarrow Aut$ refining the result automaton together with the assignments,
+The structure implicitely computed by the algorithm is a triple $ Aut= \langle OTs, States, Assigns\rangle$.
+
+Then the assignments set of $OA_1$ is $Assignments(L1, States(L1))$ and that of $OA_2$ is $Assignments(L2_{sat}, States(L2_{sat}))$. The computed triples are 
+\[Aut_1 = \langle L1_{sat}, States(L1_{sat}), Assignments(L1, States(L1))\rangle\] and \[Aut_2 = \langle L2_{sat}, States(L2_{sat}), Assignments(L2_{sat}, States(L2_{sat}))\rangle \ . \]
+
+Based on the notation of the triple, we define the function $Refine : Aut \rightarrow Aut$ refining the result automaton together with the assignments,
 \begin{align*}
@@
 
-Given that every iteration will remove some unsatisfiable transitions, $Refine$ is a monotone function. There exists a sequence $Aut^n = Refine(Aut^{n-1})$ s.t. $|Aut^n|\le |Aut^{n-1}|$.
+Given that every iteration will remove some unsatisfiable transitions, $Refine$ is a monotone function. There exists a sequence $Aut^n = Refine(Aut^{n-1})$ s.t. $|Aut^n| < |Aut^{n-1}|$.
 Let $Aut''$ contains the $OT''$ which has no more unsatisfiable transition, then there is $Aut'' = Refine(Aut'')$ and $|Aut''| = |Refine(Aut'')|$.
-
-Let the fixed points $Refine(Aut''_1) = Aut''_1$, $Refine(Aut''_2) = Aut''_2$.
-
-For the transitions set in $Aut''_1$ and $Aut''_2$, $L1''_{sat}=L1_{reach}$ and $L2''_{sat}=L2_{reach}$, we need to check their equivalence.
+Let $Aut''_1$ and $Aut''_2$ be the two
+ fixed points with $Refine(Aut''_1) = Aut''_1$, $Refine(Aut''_2) = Aut''_2$.
+
+For the transition sets in $Aut''_1$ and $Aut''_2$, $L1''_{sat}=L1_{reach}$ and $L2''_{sat}=L2_{reach}$, we need to check their equivalence.
 At the first iteration, the unsatisfiable transitions in $OA_1$ has only one case according to the relation between the assertions to check,
@@
 \end{align*}
-By induction, after removing all the transitions not in the $L2''_{sat}$, we can get that $L1_{reach}=L2_{reach}$, subsequently, $States_{L1_{reach}}=States_{L2_{reach}}$,
-$Assignments\\(L1_{reach},States_{L1_{reach}})=Assignments(L2_{reach},States_{L2_{reach}})$.
+By induction, after removing all the transitions not in $L2''_{sat}$, we obtain  $L1_{reach}=L2_{reach}$, which implies that $States_{L1_{reach}}=States_{L2_{reach}}$ and
+$$Assignments\\(L1_{reach},States_{L1_{reach}})=Assignments(L2_{reach},States_{L2_{reach}})\ .$$
+\hfill\qed
 \end{proof}
@@
 pNets.
-We also compare the practical performances of the 2 algorithms and
+We also compare the practical performances of the two algorithms and
 show the benefit gained using the smart approach.

### 2019-03-29 2017-Xudong-SMT/ActaInformatica.tex
Acta paper: minor clean-up so that the paper compiles without errors

@@
 
-\begin{proof}
+%\begin{proof}
 %  Let $pn=<...>$ be a pNet. The set of states 
@@
 %    I'm not sure if parts of it can be reused}
-\begin{proof of Theorem \ref{Th:CorrectnessWithoutAssignments}}
+\begin{proof}[Theorem \ref{Th:CorrectnessWithoutAssignments}]
 
@@
 \[\forall \ostate{\tilde{u}}\in States(L2_{reach}), \exists\ostate{\tilde{t}}\in States(L1), \ostate{\tilde{t}}=\ostate{\tilde{a_0...a_n}}=\ostate{\tilde{u}}.\]
-\noteInEric{I don't agree with the previous statement: the main loop
+\noteInEM{I don't agree with the previous statement: the main loop
   constructs L1 (resp $L2_{sat}$), note the sets of states, so this
-  argument would give you
+  argument would give you }
 

### 2019-03-29 2017-Xudong-SMT/ActaInformatica.tex
small changes to proof 2

@@
   \label{Th:CorrectnessWithoutAssignments}
-If a pNet verifying the finiteness conditions of theorem 1, and
+For a pNet verifying the finiteness conditions of theorem 1, and
 containing no assignment to state variables, then the smart  
@@
 
-\ERIC{Sketch of the proof:}
-
-%\begin{proof}
-%  Let $pn=<...>$ be a pNet. The set of states 
-%  managed by the two algorithms both are subsets of the cartesian
-%  product of the pLTS states, as defined in \pageref{def-states}. In a
-%  similar way, the set of state variables are also equal. Comparing
-%  transitions requires a little more care, because within the
-%  MakeTransitions function, fresh variables are created everytime a
-%  synchronisation vector is used (this occurs within the $MkPred$ and
-%  $matching$ functions). However, given a global state, the call of
-%  $MakeTransitions$ will always returns exactly the same set of OTs, up to
-%  renaming of these fresh variables\footnote{I think this does not
-%    need any specific proof, given that it is the same function,
-%    called with the same arguments}.
-%
-%  Let us define the following sets of OTs, as computed by the 2
-%  algorithms:
-%  \ERIC{not sure whether all these sets are useful, but it's good to
-%    have them precisely defined for the moment}
-%  \begin{itemize}
-%    \item $L1$ = original set of transitions by Algorithm 1
-%      (i.e. before line 11), 
-%    \item $L1-sat$ = original set of transitions by Algorithm 1, after
-%      satisfiability check (i.e. after line 11),
-%    \item $L1-reach$ = final set of OTs of Algorithm 1, as computed
-%      by line 12.
-%    \item $L2-sat$ = original set of transitions by Algorithm 2
-%      (i.e. before line 13), 
-%    \item $L2-reach$ = final set of OTs of Algorithm 2, as computed
-%          by line 13.
-%  \end{itemize}
-%
-%  For each of these, define $States : OT^* -> State^*$ the function
-%  computing the set of target states of a set of OTs.
-%
-%  We want to prove that $L1-reach = L2-reach$ (upto renaming of fresh
-%  variables) and $States(L1-reach) = States(L2-reach)$.
-%
-%  From the structure of the main loops of the algorithms, we know that
-%  $L1-sat \subset L2-sat$ and subsequently $States(L1-sat) \subset       
-%  States(L2-sat)$.
-%  \qed
-%\end{proof}
-%  
+% \ERIC{Sketch of the proof:}
+
 %    \medskip
@@
 \begin{proof}[Theorem \ref{Th:CorrectnessWithoutAssignments}]
+
+ Let $pn=$ be a pNet. The set of states 
+ managed by the two algorithms both are subsets of the cartesian
+ product of the pLTS states, as defined in page \pageref{def-states}. In a
+ similar way, the set of state variables attached to each state are
+ also equal. Comparing  
+ transitions requires a little more care, because within the
+ MakeTransitions function, fresh variables are created everytime a
+ synchronisation vector is used (this occurs within the $MkPred$ and
+ $matching$ functions). However, given a global state, the call of
+ $MakeTransitions$ will always returns exactly the same set of OTs, up to
+renaming of these fresh variables
 
@@
 
-For each of these, define $States: \langle OT\rangle\rightarrow\langle
-State\rangle$ which is the function computing the set of states in a
-set of OTs. Between two transition sets of the algorithms, define
+\paragraph{States:} for each of these, define $States: \langle OT\rangle\rightarrow\langle State\rangle$ which is the function computing the set of states in a
+set of OTs.
+
+Between two transition sets of the algorithms, define
 $Rename:  L1_{reach} \rightarrow L2_{reach}$ which is the function
@@
 $\ostate{\tilde{s}}=\ostate{\tilde{s_0...s_n}}$ is a composition of $n$
-PLTS states $s_{i}^{i\in [0,n]}$.
-
-From the structure of the main loop of the algorithms, we can get $States(L2_{reach})\subseteq  States(L1)$, then
+pLTS states $s_{i}^{i\in [0,n]}$.
+
+From the structure of the main loop of the algorithms, we can get that algorithm~\ref{alg1} computes less transitions than algorithm~\ref{alg3}, i.e.
+$L2_{reach}\subseteq  L1$, and as a consequence $States(L2_{reach})\subseteq  States(L1)$, so we have:
 \[\forall \ostate{\tilde{u}}\in States(L2_{reach}), \exists\ostate{\tilde{t}}\in States(L1), \ostate{\tilde{t}}=\ostate{\tilde{a_0...a_n}}=\ostate{\tilde{u}}.\]
-\noteInEM{I don't agree with the previous statement: the main loop
-  constructs L1 (resp $L2_{sat}$), note the sets of states, so this
-  argument would give you }
 
@@
   \label{Th:CorrectnessWithAssignments}
-In the general case, if a pNet contains some assignments to state variables, the smart algorithm computes 
+In the general case, if a pNet (verifying the finiteness conditions of theorem 1), contains some assignments to state variables, the smart algorithm computes 
 the same open automaton as that of Algorithm 1 up to a renaming of variables in the transition labels.
@@
 
-\TODO{Formalize the proof}
+%\TODO{Formalize the proof}
 \begin{proof}

### 2019-03-29 2017-Xudong-SMT/ActaInformatica.tex
Improve the proof of Th.2 after Skype.

@@
 with the same initial state $\ostate{\tilde{t_0}}$, this state is the
-initial state of both $L1_{reach})$ and $L2_{reach})$.
+initial state of both $L1_{reach}$ and $L2_{reach}$.
 
@@
 
-  Suppose that  $\ostate{\tilde{t}}\in States(L2_{reach})$.
-It is reachable in the result automaton of Algorithm 3, so there exists a sequence of transitions $\ostate{\tilde{t_0}}...\xrightarrow{v_j}...\ostate{\tilde{t}}$ where $Pred_j$ are all satisfiable.
-Then there exists the same state $\ostate{\tilde{t}}\in States(L1_{reach})$ and $\ostate{\tilde{t_0}}...\xrightarrow{v_i}...\ostate{\tilde{t}}$ where $Pred_i$ are all satisfiable.
+Suppose that  $\ostate{\tilde{t}}\in States(L2_{reach})$. It is reachable in the result automaton of Algorithm 3, so there exists a sequence of transitions 
+\[\ostate{\tilde{t_0}}\xrightarrow{l_1}\ostate{\tilde{t_1}}\xrightarrow{l_2}...\xrightarrow{l_{n}}\ostate{\tilde{t}}\] where in each label of the transition $Pred_{l_i}^{i\in [1,n]}$ is satisfiable.
+For the same state $\ostate{\tilde{t}}\in States(L1_{reach})$, there exists a sequence of transitions \[\ostate{\tilde{t_0}}\xrightarrow{l'_1}\ostate{\tilde{t_1}}\xrightarrow{l'_2}...\xrightarrow{l'_{n}}\ostate{\tilde{t}}\]where for each transition $Rename(\ostate{\tilde{t_{i-1}}}\xrightarrow{l_{i}}\ostate{\tilde{t_{i}}}) = \ostate{\tilde{t_{i-1}}}\xrightarrow{l'_{i}}\ostate{\tilde{t_{i}}}$ and $Pred_{l'_i}^{i\in [1,n]}$ is satisfiable.
 From the structure of the algorithms, 
-\[\forall \ostate{\tilde{t}}\in States(L2_{reach}), OT = \ostate{\tilde{t}}\xrightarrow{v}\ostate{\tilde{t'}}\in L2_{reach}\]
-\[\exists OT' = \ostate{\tilde{t}}\xrightarrow{v'}\ostate{\tilde{t'}}\in L1 \quad s.t.\quad Rename(OT') = OT.\]
-where $Pred$ and $Pred'$ are satisfiable.
-
-Then we can get a new longer sequence $\ostate{\tilde{t_0}}...\xrightarrow{v_i}...\ostate{\tilde{t'}}\xrightarrow{v'}\ostate{\tilde{t'}}$ implying that $\ostate{\tilde{t'}}\in States(L1_{reach}),OT'\in L1_{reach}$.
-So
+\[\forall \ostate{\tilde{t}}\in States(L2_{reach}), \ostate{\tilde{t}}\xrightarrow{l'_{n+1}}\ostate{\tilde{t'}}\in L2_{reach}\]
+\[\exists \ostate{\tilde{t}}\xrightarrow{l_{n+1}}\ostate{\tilde{t'}}\in L1 \quad s.t.\quad Rename(\ostate{\tilde{t}}\xrightarrow{l_{n+1}}\ostate{\tilde{t'}}) = \ostate{\tilde{t}}\xrightarrow{l'_{n+1}}\ostate{\tilde{t'}})\]
+where $Pred_{l_{n+1}}$ and $Pred_{l'_{n+1}}$ are satisfiable.
+
+Then we can get a new longer sequence \[\ostate{\tilde{t_0}}\xrightarrow{l_1}\ostate{\tilde{t_1}}\xrightarrow{l_2}...\xrightarrow{l_{n}}\ostate{\tilde{t}}\xrightarrow{l_{n+1}}\ostate{\tilde{t}}\] \[\Rightarrow\ostate{\tilde{t'}}\in States(L1_{reach})\wedge\ostate{\tilde{t}}\xrightarrow{l_{n+1}}\ostate{\tilde{t'}}\in L1_{reach}\in L1.\] So for arbitrary transition in $L2_{reach}$, there is a same transition in $L1_{reach}$ after renaming its label, then we get
 $L2_{reach}\subseteq  L1_{reach}$.
 
-%Moreover,
 Conversely,
-\[\forall OT\notin L2_{reach}, \exists OT'\in L1, Rename(OT') = OT\]
-where $Pred$ and $Pred'$ are not satisfiable. Then according to the pruning function in Algorithm 1, $OT'\notin L1_{reach}$. 
+\[\forall \ostate{\tilde{t'}}\notin States(L2_{reach}), \ostate{\tilde{t}}\xrightarrow{l'}\ostate{\tilde{t'}}\notin L2_{reach},\quad\exists \ostate{\tilde{t'}}\in States(L1), \ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L1\]
+where $Pred_{l}$ and $Pred_{l'}$ are not satisfiable.
+As pruning function in Algorithm 1 will remove all the unsatisfiable transitions, then $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\notin L1_{reach}$.
+
 As a result, we get that $L1_{reach}=L2_{reach}$, and subsequently, $States(L1_{reach})=States(L2_{reach})$.

### 2019-03-30 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf. paper (minor): moved the hyperref package to avoid name use errors at compilations
Improve the proof of Th.3 after Skype.

@@
 
-\usepackage{hyperref}
-
 \def\AlgT{\mathcal{T}}
@@
 %\usepackage{algpseudocode}
+
+\usepackage{hyperref}
 
@@
 
-%\section{}
-%\subsection{}
+%%\section{}
+%%\subsection{}
 
@@
 
-\paragraph{States:} for each of these, define $States: \langle OT\rangle\rightarrow\langle State\rangle$ which is the function computing the set of states in a
+\paragraph{States:} for each of these, define $States: \langle OT\rangle\rightarrow\langle State\rangle$ which is the function computing the set of target states in a
 set of OTs.
@@
 
-Define the function $States$ as before, and  $Assignments : \langle OT\rangle\times\langle State\rangle\rightarrow\langle Assign\rangle$ the function
+Define the function $States$ as before, and  $Assignments : \langle OT\rangle\times State\rightarrow\langle Assign\rangle$ the function
 computing the set of assignments of a global state from a given set of OTs.
 
-The structure implicitely computed by the algorithm is a triple $ Aut= \langle OTs, States, Assigns\rangle$.
-
-Then the assignments set of $OA_1$ is $Assignments(L1, States(L1))$ and that of $OA_2$ is $Assignments(L2_{sat}, States(L2_{sat}))$. The computed triples are 
-\[Aut_1 = \langle L1_{sat}, States(L1_{sat}), Assignments(L1, States(L1))\rangle\] and \[Aut_2 = \langle L2_{sat}, States(L2_{sat}), Assignments(L2_{sat}, States(L2_{sat}))\rangle \ . \]
-
-Based on the notation of the triple, we define the function $Refine : Aut \rightarrow Aut$ refining the result automaton together with the assignments,
+The structure implicitely computed by the algorithm is a triple $ Aut= \langle OTs, States,\\ Assigns\rangle$.
+
+Then the assignments set of $OA_1$ is $\{Assignments(L1, State_{i})\}^{State_{i}\in States(L1)}$ and that of $OA_2$ is $\{Assignments(L2_{sat}, State_{j})\}^{State_{j}\in States(L2_{sat})}$.
+The computed triples are
+\[Aut_1 = \langle L1_{sat}, States(L1_{sat}), \{Assignments(L1, State_{i})\}^{State_{i}\in States(L1)}\rangle\] and \[Aut_2 = \langle L2_{sat}, States(L2_{sat}), \{Assignments(L2_{sat}, State_{j})\}^{State_{j}\in States(L2_{sat})}\rangle \ .
+\]
+
+Based on the notation of the triple, we define the function $Refine : Aut \rightarrow Aut$ implementing $makeReachableSubAutomaton(S0,OTs)$, it uses the assignments of the previous step to refine the computed reachable space.
 \begin{align*}
-Refine(Aut) &=\langle OT', States(OT'), Assignments(OT', States(OT'))\rangle \\
+Refine(Aut) &=\langle L', States(L'), \{Assignments(L', State_{i})\}^{State_{i}\in States(L')}\rangle \\
 &=Aut'
 \end{align*}
-where $OT' = OT - OT_{unsat}$, $OT_{unsat}$ is the set of transitions checked unsatisfiable in this iteration.
-
-Given that every iteration will remove some unsatisfiable transitions, $Refine$ is a monotone function. There exists a sequence $Aut^n = Refine(Aut^{n-1})$ s.t. $|Aut^n| < |Aut^{n-1}|$.
-Let $Aut''$ contains the $OT''$ which has no more unsatisfiable transition, then there is $Aut'' = Refine(Aut'')$ and $|Aut''| = |Refine(Aut'')|$.
-Let $Aut''_1$ and $Aut''_2$ be the two
- fixed points with $Refine(Aut''_1) = Aut''_1$, $Refine(Aut''_2) = Aut''_2$.
-
-For the transition sets in $Aut''_1$ and $Aut''_2$, $L1''_{sat}=L1_{reach}$ and $L2''_{sat}=L2_{reach}$, we need to check their equivalence.
-At the first iteration, the unsatisfiable transitions in $OA_1$ has only one case according to the relation between the assertions to check,
+where $L' = L - L_{unsat}$, $L_{unsat}$ is the set of transitions checked unsatisfiable in this iteration.
+So there must has $|L'|<|L|$, and potentially, their target states and the corresponding assignments may be reduced:
+\[States_{L'}=\{State_{init}\}\cup \bigcup States(L'),\]
+\[Assignments_{L',States_{L'}}=\bigcup\{Assignments(L', State_{i})\}^{State_{i}\in States_{L'}} \]
+\[s.t. |States_{L'}|\le|States_{L}|\wedge|Assignments_{L',States_{L'}}|\le|Assignments_{L,States_{L}}|.\]
+
+In one iteration, satisfiability of every transition $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L$ is checked through judging whether 
+\[\bigvee_{Assign_i\in Assignments_{L, States_{L}}}(Pred_{l}\wedge Assign_{i})\text{ is true}.\]
+More transitions may be checked unsatisfiable with the reduction of the assignments set, so the function need iterate several times.
+Given that in every iteration, the number of triples decreases, $Refine$ is a monotone function.
+And there exists a sequence \[Aut^n = Refine(Aut^{n-1})\quad s.t.
+|Aut^n| < |Aut^{n-1}|.\]
+The function terminates if $Aut''$ contains the no more unsatisfiable transition, then there is the fixed-point $Aut'' = Refine(Aut'')$ and $|Aut''| = |Refine(Aut'')|$.
+
+Let $Aut''_1$ and $Aut''_2$ be the two fixed-points with $Refine(Aut''_1) = Aut''_1$, $Refine(Aut''_2) = Aut''_2$.For the transition sets in $Aut''_1$ and $Aut''_2$, $L1''_{sat}=L1_{reach}$ and $L2''_{sat}=L2_{reach}$, we need to check their equivalence.
+
+First, there is an inclusion relation between the initial assignments sets, 
 \begin{align*}
-&\quad Pred\wedge \bigvee_i Assignments_i(L1, States(L1) \text{ is false}\\
-&\quad\longrightarrow Pred\wedge \bigvee_j Assignments_j(L2_{sat}, States(L2_{sat})\text{ is false}\\
-&\Rightarrow \forall t\in L1_{unsat} \longrightarrow t\in L2_{unsat}\\
-&\Rightarrow L1_{unsat}\subseteq L2_{unsat}.
+&L2_{sat}\subseteq L1\Rightarrow States_{L2_{sat}}\subseteq State_{L1}\\
+\Rightarrow &Assignments_{L2_{sat}, States_{L2_{sat}}}\subseteq Assignments_{L1, States_{L1}}
 \end{align*}
-However, its reverse direction is not fulfilled. Recall that $L1_{sat}=L2_{sat}$, these relations can imply that,
+
+Then we see what changes have occurred during the iterations.
+In the first iteration, the inclusion relation between their assignments gives the the inclusion relation of unsatisfiable transitions, for $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}} \in L1_{unsat}$ and $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}} \in L2_{unsat},$
 \begin{align*}
-Assignments(L1, &States(L1))\supseteq Assignments(L2_{sat}, States(L2_{sat}))\\
-&\supseteq Assignments(L1_{sat}-L1_{unsat}, States(L1_{sat}-L1_{unsat}))\\
-&\supseteq Assignments(L2_{sat}-L2_{unsat}, States(L2_{sat}-L2_{unsat}))
+&\bigvee_{Assign_i\in Assignments_{L1, States_{L1}}} (Pred_{l}\wedge Assign_i)\text{ is false}\\
+\longrightarrow&\bigvee_{Assign_j\in Assignments_{L2_{sat}, States_{L2_{sat}}}} (Pred_{l}\wedge Assign_j)\text{ is false}.
 \end{align*}
-So after the first iteration, the unsatisfiable transitions in $OA_1$ has two cases,
+The relation that $\forall\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}} \in L1_{unsat},\exists\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}} \in L2_{unsat}$, implies that $L1_{unsat}\subseteq L2_{unsat}.$
+
+However, its reverse direction is not fulfilled. Recall that $L1_{sat}=L2_{sat}$, more inclusion relations of the assignments can be implied,
 \begin{align*}
-&\forall t\in L1'_{unsat} \longrightarrow t\in L2'_{unsat}\\
-\text{ or }&\forall t\in L1'_{unsat} \longrightarrow t\notin L2'_{sat}.
+Assignments_{L1, States_{L1}}&\supseteq Assignments_{L2_{sat}, States_{L2_{sat}}}\\
+&\supseteq Assignments_{L1_{sat}-L1_{unsat}, States_{(L1_{sat}-L1_{unsat})}}\\
+&\supseteq Assignments_{L2_{sat}-L2_{unsat}, States_{(L2_{sat}-L2_{unsat})}}
 \end{align*}
-By induction, after removing all the transitions not in $L2''_{sat}$, we obtain  $L1_{reach}=L2_{reach}$, which implies that $States_{L1_{reach}}=States_{L2_{reach}}$ and
-$$Assignments\\(L1_{reach},States_{L1_{reach}})=Assignments(L2_{reach},States_{L2_{reach}})\ .$$
+
+Let $L1'_{sat}=L1_{sat}-L1_{unsat}$ and $L2'_{sat}=L2_{sat}-L2_{unsat}$
+Then in the next iteration, the unsatisfiable transition $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}$ removed from $L1'_{sat}$ might be the same transition (up to renaming) removed from $L2'_{sat}$, that is
+\[\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L1'_{unsat} \longrightarrow \ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L2'_{unsat}.\]
+Or it is the transition has not removed in the last iteration because of 
+\[Assignments_{L2_{sat}, States_{L2_{sat}}}\subseteq Assignments_{L1, States_{L1}}.\] 
+We have already proved that 
+\[Assignments_{L1'_{sat}, States_{L1'_{sat}}}\subseteq Assignments_{L2_{sat}, States_{L2_{sat}}},\]
+so those transitions will be removed this time, that is
+\[\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L1'_{unsat} \longrightarrow \ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\notin L2_{sat}.\]
+
+By induction, if there is no more unsatiable transitions in $L2''_{sat}$, $L1''_{sat}$ continues removing all the transitions not in $L2''_{sat}$, until $L1_{reach}=L2_{reach}$, which implies that $States_{L1_{reach}}=States_{L2_{reach}}$ and
+$$Assignments_{L1_{reach},States_{L1_{reach}}}=Assignments_{L2_{reach},States_{L2_{reach}}}.$$
 \hfill\qed
@@
 
-  \medskip
-  \noteInEM{I keep below the original proof draft from Xudong, though
-    think it does not apply any more}
+%  \medskip
+%  \noteInEM{I keep below the original proof draft from Xudong, though
+%    think it does not apply any more}
 
@@
   \caption{The two open automata}
+  %% \noteSB{I guess pNets in this figure have to be replaced by open
+  %%   automata}
   \label{schema:enable-OAs}

### 2019-03-30 2017-Xudong-SMT/ActaInformatica.tex
Correct typos in the proof of Th.3.

@@
 \begin{proof}
-In Theorem 2, we have already proved the result automata $OA_1$ and $OA_2$ of the two algorithm are the same without the assignments.
-
-Define the function $States$ as before, and  $Assignments : \langle OT\rangle\times State\rightarrow\langle Assign\rangle$ the function
+In Theorem 2, we have already proved that the result automata $OA_1$ and $OA_2$ of two algorithms are the same if the pNet contains no assignment to its state variables.
+
+We define the function $States$ as before, and the function $Assignments : \langle OT\rangle\times State\rightarrow\langle Assign\rangle$
 computing the set of assignments of a global state from a given set of OTs.
 
-The structure implicitely computed by the algorithm is a triple $ Aut= \langle OTs, States,\\ Assigns\rangle$.
-
-Then the assignments set of $OA_1$ is $\{Assignments(L1, State_{i})\}^{State_{i}\in States(L1)}$ and that of $OA_2$ is $\{Assignments(L2_{sat}, State_{j})\}^{State_{j}\in States(L2_{sat})}$.
-The computed triples are
+The structure implicitly computed by the algorithm is a triple $ Aut= \langle OTs, States,\\ Assigns\rangle$.
+
+Then the assignments set of $OA_1$ is $\{Assignments(L1, State_{i})\}^{State_{i}\in States(L1)}$ and $OA_2$ is $\{Assignments(L2_{sat}, State_{j})\}^{State_{j}\in States(L2_{sat})}$.
+The result triples should be
 \[Aut_1 = \langle L1_{sat}, States(L1_{sat}), \{Assignments(L1, State_{i})\}^{State_{i}\in States(L1)}\rangle\] and \[Aut_2 = \langle L2_{sat}, States(L2_{sat}), \{Assignments(L2_{sat}, State_{j})\}^{State_{j}\in States(L2_{sat})}\rangle \ .
@@
 
-Based on the notation of the triple, we define the function $Refine : Aut \rightarrow Aut$ implementing $makeReachableSubAutomaton(S0,OTs)$, it uses the assignments of the previous step to refine the computed reachable space.
+Basing on the notation of the triple, we define the function $Refine : Aut \rightarrow Aut$ implementing $makeReachableSubAutomaton(S0,OTs)$, it uses the assignments of the previous step to refine the computed reachable space.
 \begin{align*}
@@
 \end{align*}
-where $L' = L - L_{unsat}$, $L_{unsat}$ is the set of transitions checked unsatisfiable in this iteration.
-So there must has $|L'|<|L|$, and potentially, their target states and the corresponding assignments may be reduced:
+where $L' = L - L_{unsat}$, $L_{unsat}$ is the set of unsatisfiable transitions checked in this iteration.
+So there must have $|L'|<|L|$, and potentially, their target states and corresponding assignments could be reduced:
 \[States_{L'}=\{State_{init}\}\cup \bigcup States(L'),\]
@@
 
-In one iteration, satisfiability of every transition $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L$ is checked through judging whether 
+In one single iteration, satisfiability of a transition $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L$ is checked through whether 
 \[\bigvee_{Assign_i\in Assignments_{L, States_{L}}}(Pred_{l}\wedge Assign_{i})\text{ is true}.\]
-More transitions may be checked unsatisfiable with the reduction of the assignments set, so the function need iterate several times.
-Given that in every iteration, the number of triples decreases, $Refine$ is a monotone function.
+More transitions could be unsatisfiable after the reduction of the assignments set, so the function need iterate several times.
+Given that in each iteration, the number of triples decreases, so $Refine$ is a monotone function.
 And there exists a sequence \[Aut^n = Refine(Aut^{n-1})\quad s.t.
 |Aut^n| < |Aut^{n-1}|.\]
-The function terminates if $Aut''$ contains the no more unsatisfiable transition, then there is the fixed-point $Aut'' = Refine(Aut'')$ and $|Aut''| = |Refine(Aut'')|$.
-
-Let $Aut''_1$ and $Aut''_2$ be the two fixed-points with $Refine(Aut''_1) = Aut''_1$, $Refine(Aut''_2) = Aut''_2$.For the transition sets in $Aut''_1$ and $Aut''_2$, $L1''_{sat}=L1_{reach}$ and $L2''_{sat}=L2_{reach}$, we need to check their equivalence.
+The function terminates if $Aut''$ contains no more unsatisfiable transition, then there is a fixed-point $Aut'' = Refine(Aut'')$ and $|Aut''| = |Refine(Aut'')|$.
+
+Let $Aut''_1$ and $Aut''_2$ be two fixed-points that $Refine(Aut''_1) = Aut''_1$, $Refine(Aut''_2) = Aut''_2$.
+Focusing on the transition sets in $Aut''_1$ and $Aut''_2$, $L1''_{sat}=L1_{reach}$ and $L2''_{sat}=L2_{reach}$, we need to check their equivalence.
 
@@
 
-Then we see what changes have occurred during the iterations.
-In the first iteration, the inclusion relation between their assignments gives the the inclusion relation of unsatisfiable transitions, for $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}} \in L1_{unsat}$ and $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}} \in L2_{unsat},$
+Then we come to see what changes have occurred during the iterations.
+In the first iteration, the inclusion relation between their assignments implies an inclusion relation of unsatisfiable transitions.
+If there are two transitions $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}} \in L1_{unsat}$ and $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}} \in L2_{unsat},$ then
 \begin{align*}
@@
 Let $L1'_{sat}=L1_{sat}-L1_{unsat}$ and $L2'_{sat}=L2_{sat}-L2_{unsat}$
-Then in the next iteration, the unsatisfiable transition $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}$ removed from $L1'_{sat}$ might be the same transition (up to renaming) removed from $L2'_{sat}$, that is
+Then in the next iteration, the unsatisfiable transition $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}$ removed from $L1'_{sat}$ might be the same transition (up to renaming) removed from $L2'_{sat}$.
+In this case,
 \[\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L1'_{unsat} \longrightarrow \ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L2'_{unsat}.\]
@@
 \[Assignments_{L1'_{sat}, States_{L1'_{sat}}}\subseteq Assignments_{L2_{sat}, States_{L2_{sat}}},\]
-so those transitions will be removed this time, that is
+so those transitions will be removed this time. In this case,
 \[\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L1'_{unsat} \longrightarrow \ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\notin L2_{sat}.\]
 
-By induction, if there is no more unsatiable transitions in $L2''_{sat}$, $L1''_{sat}$ continues removing all the transitions not in $L2''_{sat}$, until $L1_{reach}=L2_{reach}$, which implies that $States_{L1_{reach}}=States_{L2_{reach}}$ and
+By induction, if there is no more unsatisfiable transitions in $L2''_{sat}$, $L1''_{sat}$ continues removing all the transitions not in $L2''_{sat}$, until $L1_{reach}=L2_{reach}$.
+It implies that $States_{L1_{reach}}=States_{L2_{reach}}$ and
 $$Assignments_{L1_{reach},States_{L1_{reach}}}=Assignments_{L2_{reach},States_{L2_{reach}}}.$$

### 2019-03-30 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf. paper: somewhat shortend the BIP architecture presentation

--- 2019-03-29 2017-Xudong-SMT/ActaInformatica.tex
@@
 
-\newcommand{\noteSB}[2][color=green!40, size=\tiny]{\todo[#1]{{\bf
-      Note: } {#2}}}
+\newcommand{\noteSB}[2][color=green!40, size=\tiny]{\todo[#1]{{\bf Simon: } {#2}}}
 \newcommand{\noteEM}[2][color=blue!40, size=\tiny]{\todo[#1]{{\bf Eric: } {#2}}}
@@
 
-\input{XFIG/macros.tex}         % Definitions of macros used in XFig figures
+\input{ActaXFIG/macros.tex}         % Definitions of macros used in XFig figures
 \usepackage{macrospNets}
-
-\usepackage{hyperref}
 
@@
 Figure~\ref{schema:enable-OAs}.
+\noteSB{I guess pNets in this figure have to be replaced by open
+  automata}
 Note that although these automata look very similar to the PLTS
@@
 Figure~\ref{schema:enable-composed}. Its open automaton is shown in
-Figure~\ref{schema:enable3bis}. Building the symmetric system ``(P>>Q)>>R'' in a similar
+Figure~\ref{schema:enable3bis}. Building the symmetric system \noteSB{Should this be typeset in math mode?}``(P>>Q)>>R'' in a similar
 way will allow us to prove that they are bisimilar (the Enable
@@
 
-\subsection{BIP FailureTimer Architecture}
+\subsection{BIP Failure Monitor Architecture}
 \label{section:FailureTimer}
@@
 
-As a running example we use the Failure Monitor architecture from the
+In this section, we present the Failure Monitor architecture from the
 CubETH nanosatellite on-board software
@@
 Failure Monitor architecture used in~\cite{CubETH-case-study}.
-Contrary to standard BIP models, architectures comprise one or several
-\emph{operand} components, whereof only the set of \emph{ports} is
-given.  Here, the operand component is $\NameOprnd$ and its interface
-consists of the ports $\PortResume$ and $\PortFail$.
-The two \emph{coordinator} components\mdash $\NameCtrl$ and
-$\NameTimer$\mdash are standard BIP components insofar as they also
-have their \emph{behaviour} specified by finite automata extended with
+%
+The architecture consists of 2 \emph{coordinator components}
+($\NameCtrl$ and $\NameTimer$, for \emph{Control} and \emph{Timer},
+respectively), 5 \emph{dangling ports} ($\PortFail$, $\PortResume$,
+$\PortTick$, $\PortReset$ and $\PortAsk$) and 5 connectors.
+%
+%% Contrary to standard BIP models, architectures comprise one or several
+%% \emph{operand} components, whereof only the set of \emph{ports} is
+%% given.  Here, the operand component is $\NameOprnd$ and its interface
+%% consists of the ports $\PortResume$ and $\PortFail$.
+%% The two \emph{coordinator} components\mdash $\NameCtrl$ and
+%% $\NameTimer$\mdash are standard
+The  \emph{behaviour} of BIP components %% insofar as they also
+%% have their 
+is specified by finite automata extended with
 local data variables.  Transitions of these automata are labelled with
 the ports of the corresponding components, Boolean guards and update
-functions on local variables.  For instance, the loop transition
-$t_1 \goesto{\PortTick, [t < Max], t:=t+1} t_1$
-in the $\NameTimer$ component is labelled by the port $\PortTick$. It
-can be fired only when the current value of the local variable $t$ is
-lower than $Max$.  Upon firing, this transition increments the value
-of $t$ by $1$.  When omitted, the default guard (\resp update
-function) is the constant predicate $\true$ (\resp the $\mathit{skip}$
-operator).  The constant $\mathrm{Max}$ above, is a parameter of the
-architecture.
-
-Connectors are hierarchical, tree-like structures with component ports
-at the leaves.  They define sets of \emph{interactions}, based on the
-attributes of the connected ports~\cite{BliSif08-acp-tc}, which may be
+functions on local variables.  %% For instance, the loop transition
+%% $t_1 \goesto{\PortTick, [t < Max], t:=t+1} t_1$
+%% in the $\NameTimer$ component is labelled by the port $\PortTick$. It
+%% can be fired only when the current value of the local variable $t$ is
+%% lower than $Max$.  Upon firing, this transition increments the value
+%% of $t$ by $1$.  When omitted, the default guard (\resp update
+%% function) is the constant predicate $\true$ (\resp the $\mathit{skip}$
+%% operator).  The constant $\mathrm{Max}$ above, is a parameter of the
+%% architecture.
+
+%% Connectors are hierarchical, tree-like structures with component ports
+%% at the leaves.  They define sets of \emph{interactions}, 
+Based on the
+attributes of the connected ports, which may be
 either \emph{triggers} (triangles in Figure~\ref{schema:ArchFailure:BIP})
-or \emph{synchrons} (bullets in Figure~\ref{schema:ArchFailure:BIP}).
+or \emph{synchrons} (bullets in Figure~\ref{schema:ArchFailure:BIP}),
 %
-If all the sub-connectors of a connector are synchrons, then an
-interaction may be executed by the connector only if each subconnector
-can contribute.
-%
-If at least one of the sub-connectors is a trigger, then any
-interaction consisting of contributions of any set of sub-connectors,
-\emph{involving at least one of the triggers}, can be executed.
+connectors specify the syncrhonisations (also called
+\emph{interactions}) between the transitions of the individual
+components.  Intuitively, triggers can initiate interactions, whereas
+synchrons can only join.  If a connector does not have triggers, all
+the involved ports must synchronise~\cite{BliSif08-acp-tc}.
+%% %
+%% If all the sub-connectors of a connector are synchrons, then an
+%% interaction may be executed by the connector only if each subconnector
+%% can contribute.
+%% %
+%% If at least one of the sub-connectors is a trigger, then any
+%% interaction consisting of contributions of any set of sub-connectors,
+%% \emph{involving at least one of the triggers}, can be executed.
 %
@@
 particular, this means that whenever the transition 
-$c_0 \goesto{\PortFail} c_1$ is fired, so is the transition
-$t_0 \goesto{\PortStart, t:=0} t_1$,
+$\cstate{0} \goesto{\PortFail} \cstate{1}$ is fired, so is the transition
+$\tstate{0} \goesto{\PortStart, t:=0} \tstate{1}$,
 initialising the timer.  The binary connector $\NameTimer.\PortStart
 \bullet\!\!\!-\!\!\!-\!\!\!\bullet \NameCtrl.\PortFail$ is a
-sub-connector of a hierarchical connector, where the port
+sub-connector of a hierarchical connector, where the dangling port
 $\NameOprnd.\PortFail$ is a trigger.  Thus, the above interaction can
@@
 
-Application of the Failure Monitor architecture ensures that, whenever
+\hl{Application of the Failure Monitor architecture ensures that, whenever
 a failure is registered in the operand component, the system will be
 reset, unless a resumption is registered within $\mathrm{Max}$ time
-units (more details in Secion~\ref{section:FailureTimer}).
+units (more details in Section~\ref{section:FailureTimer}).}
 
@@
 above Failure Monitor architecture.  This encoding is structural: each
-coordinator component is encoded as a PLTS and the operand
-component as a hole; connectors of the BIP model are encoded as
-synchronisation vectors.  Each connector that does not involve
-triggers is trivially encoded by a synchronisation vector comprising
-the same ports.  In order to encode the semantics of the connectors
-involving triggers, we 1)~in the PLTS encoding the coordinator
-components, add loop transitions to ensure that all ports involved in
-such connectors are enabled in all states, 2)~associate a Boolean
-value to each of these ports: the original transitions carry the value
-$\true$ (\eg $c_0 \goesto{\PortFail(\true)} c_1$) and the
-added loops carry the value $\false$ (\eg $c_2
-\goesto{\PortFail(\false)} c_2$), 3)~add to the corresponding
-synchronisation vectors the Boolean predicate encoding the connector
-structure.  For example, $SV0$ encodes the connector discussed above:
-the predicate $(b1=b2) \land (b1\lor b2 \Rightarrow b0)$ means that the
-``true'' transitions $\NameCtrl.\PortFail$ and $\NameTimer.\PortStart$
-can only fire together ($b1 = b2$) and whenever one of them fires,
+coordinator component is encoded as a PLTS; dangling ports are encoded as actions of the hole;
+%%  and the operand component as a hole;
+connectors of the BIP model are encoded as synchronisation vectors.
+Each connector that does not involve triggers is trivially encoded by
+a synchronisation vector comprising the same ports ($SV2$, $SV3$ and
+$SV4$).  In order to encode the semantics of the connectors involving
+triggers, we use the classical approach where non-participation of a
+port in an interaction is simulated by an additional loop
+transition~\cite{milner83-calculi}.  To this end, we consider an
+action algebra involving additional Boolean variables: the effective
+transitions carry the value $\true$ (\eg $\cstate{0}
+\goesto{\PortFail(\true)} \cstate{1}$), whereas the added loops carry
+the value $\false$ (\eg $\cstate{2} \goesto{\PortFail(\false)}
+\cstate{2}$).  In the synchronisation vectors, we use these variables
+to encode the connector structure as a Boolean predicate.  For
+example, $SV0$ encodes the connector discussed above: the predicate
+$(b1=b2) \land (b1\lor b2 \Rightarrow b0)$ means that the ``true''
+transitions $\NameCtrl.\PortFail$ and $\NameTimer.\PortStart$ can only
+fire together ($b1 = b2$) and whenever one of them fires,
 $\NameOprnd.\PortFail$ must fire also ($b1 \lor b2 \Rightarrow b0$).
@@
 %
-\noteEM{Decide later if this is still useful}Although, for the sake of brevity, we omit priorities from the
-encoding, this can be easily achieved, by introducing additional
-Boolean variables for relevant ports~\cite{BarBliu15-offer-scico}.
+\noteEM{Decide later if this is still useful}Although, for the sake of
+brevity, we omit priorities from the encoding, this can be easily
+achieved, by introducing another set of additional Boolean variables
+for relevant ports~\cite{BarBliu15-offer-scico}.
 

### 2019-03-30 2017-Xudong-SMT/ActaInformatica.tex

@@
 \begin{proof}
-In Theorem 2, we have already proved the result automata $OA_1$ and $OA_2$ of the two algorithm are the same without the assignments.
-
-Define the function $States$ as before, and  $Assignments : \langle OT\rangle\times\langle State\rangle\rightarrow\langle Assign\rangle$ the function
+In Theorem 2, we have already proved that the result automata $OA_1$ and $OA_2$ of two algorithms are the same if the pNet contains no assignment to its state variables.
+
+We define the function $States$ as before, and the function $Assignments : \langle OT\rangle\times State\rightarrow\langle Assign\rangle$
 computing the set of assignments of a global state from a given set of OTs.
 
-The structure implicitely computed by the algorithm is a triple $ Aut= \langle OTs, States, Assigns\rangle$.
-
-Then the assignments set of $OA_1$ is $Assignments(L1, States(L1))$ and that of $OA_2$ is $Assignments(L2_{sat}, States(L2_{sat}))$. The computed triples are 
-\[Aut_1 = \langle L1_{sat}, States(L1_{sat}), Assignments(L1, States(L1))\rangle\] and \[Aut_2 = \langle L2_{sat}, States(L2_{sat}), Assignments(L2_{sat}, States(L2_{sat}))\rangle \ . \]
-
-Based on the notation of the triple, we define the function $Refine : Aut \rightarrow Aut$ refining the result automaton together with the assignments,
+The structure implicitly computed by the algorithm is a triple $ Aut= \langle OTs, States,\\ Assigns\rangle$.
+
+Then the assignments set of $OA_1$ is $\{Assignments(L1, State_{i})\}^{State_{i}\in States(L1)}$ and $OA_2$ is $\{Assignments(L2_{sat}, State_{j})\}^{State_{j}\in States(L2_{sat})}$.
+The result triples should be
+\[Aut_1 = \langle L1_{sat}, States(L1_{sat}), \{Assignments(L1, State_{i})\}^{State_{i}\in States(L1)}\rangle\] and \[Aut_2 = \langle L2_{sat}, States(L2_{sat}), \{Assignments(L2_{sat}, State_{j})\}^{State_{j}\in States(L2_{sat})}\rangle \ .
+\]
+
+Basing on the notation of the triple, we define the function $Refine : Aut \rightarrow Aut$ implementing $makeReachableSubAutomaton(S0,OTs)$, it uses the assignments of the previous step to refine the computed reachable space.
 \begin{align*}
-Refine(Aut) &=\langle OT', States(OT'), Assignments(OT', States(OT'))\rangle \\
+Refine(Aut) &=\langle L', States(L'), \{Assignments(L', State_{i})\}^{State_{i}\in States(L')}\rangle \\
 &=Aut'
 \end{align*}
-where $OT' = OT - OT_{unsat}$, $OT_{unsat}$ is the set of transitions checked unsatisfiable in this iteration.
-
-Given that every iteration will remove some unsatisfiable transitions, $Refine$ is a monotone function. There exists a sequence $Aut^n = Refine(Aut^{n-1})$ s.t. $|Aut^n| < |Aut^{n-1}|$.
-Let $Aut''$ contains the $OT''$ which has no more unsatisfiable transition, then there is $Aut'' = Refine(Aut'')$ and $|Aut''| = |Refine(Aut'')|$.
-Let $Aut''_1$ and $Aut''_2$ be the two
- fixed points with $Refine(Aut''_1) = Aut''_1$, $Refine(Aut''_2) = Aut''_2$.
-
-For the transition sets in $Aut''_1$ and $Aut''_2$, $L1''_{sat}=L1_{reach}$ and $L2''_{sat}=L2_{reach}$, we need to check their equivalence.
-At the first iteration, the unsatisfiable transitions in $OA_1$ has only one case according to the relation between the assertions to check,
+where $L' = L - L_{unsat}$, $L_{unsat}$ is the set of unsatisfiable transitions checked in this iteration.
+So there must have $|L'|<|L|$, and potentially, their target states and corresponding assignments could be reduced:
+\[States_{L'}=\{State_{init}\}\cup \bigcup States(L'),\]
+\[Assignments_{L',States_{L'}}=\bigcup\{Assignments(L', State_{i})\}^{State_{i}\in States_{L'}} \]
+\[s.t. |States_{L'}|\le|States_{L}|\wedge|Assignments_{L',States_{L'}}|\le|Assignments_{L,States_{L}}|.\]
+
+In one single iteration, satisfiability of a transition $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L$ is checked through whether 
+\[\bigvee_{Assign_i\in Assignments_{L, States_{L}}}(Pred_{l}\wedge Assign_{i})\text{ is true}.\]
+More transitions could be unsatisfiable after the reduction of the assignments set, so the function need iterate several times.
+Given that in each iteration, the number of triples decreases, so $Refine$ is a monotone function.
+And there exists a sequence \[Aut^n = Refine(Aut^{n-1})\quad s.t.
+|Aut^n| < |Aut^{n-1}|.\]
+The function terminates if $Aut''$ contains no more unsatisfiable transition, then there is a fixed-point $Aut'' = Refine(Aut'')$ and $|Aut''| = |Refine(Aut'')|$.
+
+Let $Aut''_1$ and $Aut''_2$ be two fixed-points that $Refine(Aut''_1) = Aut''_1$, $Refine(Aut''_2) = Aut''_2$.
+Focusing on the transition sets in $Aut''_1$ and $Aut''_2$, $L1''_{sat}=L1_{reach}$ and $L2''_{sat}=L2_{reach}$, we need to check their equivalence.
+
+First, there is an inclusion relation between the initial assignments sets, 
 \begin{align*}
-&\quad Pred\wedge \bigvee_i Assignments_i(L1, States(L1) \text{ is false}\\
-&\quad\longrightarrow Pred\wedge \bigvee_j Assignments_j(L2_{sat}, States(L2_{sat})\text{ is false}\\
-&\Rightarrow \forall t\in L1_{unsat} \longrightarrow t\in L2_{unsat}\\
-&\Rightarrow L1_{unsat}\subseteq L2_{unsat}.
+&L2_{sat}\subseteq L1\Rightarrow States_{L2_{sat}}\subseteq State_{L1}\\
+\Rightarrow &Assignments_{L2_{sat}, States_{L2_{sat}}}\subseteq Assignments_{L1, States_{L1}}
 \end{align*}
-However, its reverse direction is not fulfilled. Recall that $L1_{sat}=L2_{sat}$, these relations can imply that,
+
+Then we come to see what changes have occurred during the iterations.
+In the first iteration, the inclusion relation between their assignments implies an inclusion relation of unsatisfiable transitions.
+If there are two transitions $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}} \in L1_{unsat}$ and $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}} \in L2_{unsat},$ then
 \begin{align*}
-Assignments(L1, &States(L1))\supseteq Assignments(L2_{sat}, States(L2_{sat}))\\
-&\supseteq Assignments(L1_{sat}-L1_{unsat}, States(L1_{sat}-L1_{unsat}))\\
-&\supseteq Assignments(L2_{sat}-L2_{unsat}, States(L2_{sat}-L2_{unsat}))
+&\bigvee_{Assign_i\in Assignments_{L1, States_{L1}}} (Pred_{l}\wedge Assign_i)\text{ is false}\\
+\longrightarrow&\bigvee_{Assign_j\in Assignments_{L2_{sat}, States_{L2_{sat}}}} (Pred_{l}\wedge Assign_j)\text{ is false}.
 \end{align*}
-So after the first iteration, the unsatisfiable transitions in $OA_1$ has two cases,
+The relation that $\forall\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}} \in L1_{unsat},\exists\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}} \in L2_{unsat}$, implies that $L1_{unsat}\subseteq L2_{unsat}.$
+
+However, its reverse direction is not fulfilled. Recall that $L1_{sat}=L2_{sat}$, more inclusion relations of the assignments can be implied,
 \begin{align*}
-&\forall t\in L1'_{unsat} \longrightarrow t\in L2'_{unsat}\\
-\text{ or }&\forall t\in L1'_{unsat} \longrightarrow t\notin L2'_{sat}.
+Assignments_{L1, States_{L1}}&\supseteq Assignments_{L2_{sat}, States_{L2_{sat}}}\\
+&\supseteq Assignments_{L1_{sat}-L1_{unsat}, States_{(L1_{sat}-L1_{unsat})}}\\
+&\supseteq Assignments_{L2_{sat}-L2_{unsat}, States_{(L2_{sat}-L2_{unsat})}}
 \end{align*}
-By induction, after removing all the transitions not in $L2''_{sat}$, we obtain  $L1_{reach}=L2_{reach}$, which implies that $States_{L1_{reach}}=States_{L2_{reach}}$ and
-$$Assignments\\(L1_{reach},States_{L1_{reach}})=Assignments(L2_{reach},States_{L2_{reach}})\ .$$
+
+Let $L1'_{sat}=L1_{sat}-L1_{unsat}$ and $L2'_{sat}=L2_{sat}-L2_{unsat}$
+Then in the next iteration, the unsatisfiable transition $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}$ removed from $L1'_{sat}$ might be the same transition (up to renaming) removed from $L2'_{sat}$.
+In this case,
+\[\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L1'_{unsat} \longrightarrow \ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L2'_{unsat}.\]
+Or it is the transition has not removed in the last iteration because of 
+\[Assignments_{L2_{sat}, States_{L2_{sat}}}\subseteq Assignments_{L1, States_{L1}}.\] 
+We have already proved that 
+\[Assignments_{L1'_{sat}, States_{L1'_{sat}}}\subseteq Assignments_{L2_{sat}, States_{L2_{sat}}},\]
+so those transitions will be removed this time. In this case,
+\[\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L1'_{unsat} \longrightarrow \ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\notin L2_{sat}.\]
+
+By induction, if there is no more unsatisfiable transitions in $L2''_{sat}$, $L1''_{sat}$ continues removing all the transitions not in $L2''_{sat}$, until $L1_{reach}=L2_{reach}$.
+It implies that $States_{L1_{reach}}=States_{L2_{reach}}$ and
+$$Assignments_{L1_{reach},States_{L1_{reach}}}=Assignments_{L2_{reach},States_{L2_{reach}}}.$$
 \hfill\qed

### 2019-03-30 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf. paper: simplified the discussion of BIP architectures

@@
 %% architecture.
+Although this is not visible in the figure, below we will assume that
+the dangling ports $\PortFail$ and $\PortResume$ belong to the operand
+component, whereas the dangling ports $\PortTick$, $\PortAsk$ and
+$\PortReset$ represent actions of the environment.
 
@@
 
-\hl{Application of the Failure Monitor architecture ensures that, whenever
-a failure is registered in the operand component, the system will be
-reset, unless a resumption is registered within $\mathrm{Max}$ time
-units (more details in Section~\ref{section:FailureTimer}).}
+Intuitively, application of the Failure Monitor architecture ensures
+that, whenever a failure is registered in the operand component, the
+system will be reset, unless a resumption is registered within
+$\mathrm{Max}$ time units.  Formally, this statement is decomposed
+into several properties, among which 
+%
+1)~the safety property \emph{``There is always a possibility to reset
+  the system after a single failure''} (\ie without additional
+failures having to occur in the meantime) specified using CTL as
+%
+\begin{equation}
+  \label{eq:FM:safety}
+  \AG
+  \bigl(\PortFail \rightarrow
+  \EX \EU[]{\lnot \PortFail}{\PortReset}\bigr)
+\end{equation}
+%
+and 2)~the liveness property \emph{``a reset will be fired when asked
+  for by a timeout''}:
+%
+\begin{equation}
+  \label{eq:FM:liveness}
+  \mathtt{AG}(\PortAsk \rightarrow \mathtt{AF}\ \PortReset).
+\end{equation}
+%
+Additional properties are provided in~\cite{Avocs-RR}.
+
+%% \TODO{it would be good to express here maybe 2 properties of the
+%%   architecture, maybe one taken from the original study, and another
+%%   one involving the timer data (number of ticks ?)}
 
@@
 above Failure Monitor architecture.  This encoding is structural: each
-coordinator component is encoded as a PLTS; dangling ports are encoded as actions of the hole;
+coordinator component is encoded as a PLTS; dangling ports belonging
+to the operand component are encoded as actions of the hole; 
 %%  and the operand component as a hole;
-connectors of the BIP model are encoded as synchronisation vectors.
+connectors of the BIP model are encoded as synchronisation vectors,
+\noteSB{Eric, please check whether this is ok.}\hl{with ports
+  representing the actions of the environment used as global actions}.
 Each connector that does not involve triggers is trivially encoded by
@@
 $SV4$).  In order to encode the semantics of the connectors involving
-triggers, we use the classical approach where non-participation of a
-port in an interaction is simulated by an additional loop
-transition~\cite{milner83-calculi}.  To this end, we consider an
-action algebra involving additional Boolean variables: the effective
-transitions carry the value $\true$ (\eg $\cstate{0}
+triggers, we use (in $SV0$ and $SV1$) the classical approach where
+non-participation of a port in an interaction is simulated by an
+additional loop transition~\cite{milner83-calculi}.  To this end, we
+consider an action algebra involving additional Boolean variables: the
+effective transitions carry the value $\true$ (\eg $\cstate{0}
 \goesto{\PortFail(\true)} \cstate{1}$), whereas the added loops carry
@@
 3 reachable global states (out of the possible 6) and 12 open
-transitions, is shown in Figure~\ref{schema:resultOA1}.
+transitions, is shown in Figure~\ref{schema:resultOA1}.\noteSB{Eric, in the state 20, $b0$ should always be $false$: $\PortFail(true)$ is not possible in Control, and the safety property (\ref{eq:FM:safety}) does not hold otherwise.}
 
@@
 
-Failure Monitor enforces \noteEM{NO!!!}1)~the safety property \emph{``the
-  system reset never happens, unless asked for by a timeout
-  following a failure''}, formalised in CTL by
-%
-\[
-\varphi \land \mathtt{AG} (\PortReset \rightarrow \varphi),
-\quad\text{where}\
-%
-\varphi = \mathtt{A} [\lnot \PortReset\ \mathtt{W}\ \PortAsk]
-\land \mathtt{A} [\lnot \PortAsk\ \mathtt{W}\ \PortFail],
-\]
-%
-($\mathtt{W}$ being the \emph{weak until} operator) and 2)~the
-liveness property \emph{``a reset will be fired when asked for by
-  a timeout''}:
-%
-$\mathtt{AG}(\PortAsk \rightarrow \mathtt{AF}\ \PortReset)$.
-%
-The satisfaction of the safety property could be established by
-applying symbolic model checking techniques.  However, in this
-example, it is obvious by inspection of the open automaton.  The
-satisfaction of the liveness property relies on the above observation
+The satisfaction of the safety property (\ref{eq:FM:safety}) could be
+established by applying symbolic model checking techniques.  However,
+in this example, it is obvious by inspection of the open automaton.
+The satisfaction of the liveness property relies on the observation
 that in the state $\ostate{s2,t0}$ only the reset transition involves
@@
 
-The safety
-property \emph{``There is always a possibility to reset the system
-  after a single failure''} (\ie without
-  additional failures having to occur in the meantime) enforced by the
-  Failure Monitor architecture can be specified using CTL as
-    $\AG
-\bigl(\PortFail \rightarrow \EX \EU[]{\lnot \PortFail}{
-  \PortReset}\bigr)$.  Additional properties are provided in~\cite{Avocs-RR}.
-
-%% \TODO{it would be good to express here maybe 2 properties of the
-%%   architecture, maybe one taken from the original study, and another
-%%   one involving the timer data (number of ticks ?)}
-
-\subsection{Composing Two FailureTimer BIP Architectures}
+\subsection{Composing Two Failure Monitor BIP Architectures}
 \label{section:use-case:Double}
 
-In the conception of the nanosatellite software \cite{CubETH-case-study}, the FailureTimer architecture was used to control several processes
-communicating on the common bus. Timeout signals (``$ask$''), resets,
-and the passing of time ($tick$) were synchronised in the global
-system.
-In this section, we use a combination of 2 FailureTimer architectures
-to demonstrate how the encoding works, and as a slightly larger
-example to show how the approach scales up.
+%% In the design of the nanosatellite software \cite{CubETH-case-study}, the Failure Monitor architecture was used to control several processes
+%% communicating through a common bus. Timeout signals (``$ask$''), resets,
+%% and the passing of time ($tick$) were synchronised in the global
+%% system.
+In this section, we use a combination of two Failure Monitor
+architectures shown in Figure~\ref{schema:ArchFailure:BIP:Double}
+%% to demonstrate how the encoding works, and
+as a slightly larger example to show how the approach scales up.  In
+this example, each of the two instances of the architecture is applied
+to a corresponding operand component.  Hence, the dangling ports
+$\PortFail$ and $\PortReset$ are duplicated accordingly.  On the
+contrary, the environment actions $\PortTick$, $\PortAsk$ and
+$\PortReset$ are shared.  For a detailed presentation of the
+architecture composition, we refer the reader to
+\cite{AttieBBJS16-architectures-faoc}.
 
@@
 
-In Figure~\ref{schema:ArchFailure:BIP:Double} we show the combination
-of two FailureTimer architectures, with their respective controlled
-processes.
-In Figure~\ref{schema:ArchFailure:Double:OA} we show the resulting
-open automaton. It indicates that the two timers are forced to
-be synchronous: each can only tick after the other has also started,
-and then they will tick, reset, and timeout, synchronously.
-
-This is a very strong assumption, and we are working on a more
+%% In Figure~\ref{schema:ArchFailure:BIP:Double} we show the combination
+%% of two Failure Monitor architectures, with their respective controlled
+%% processes.
+In Figure~\ref{schema:ArchFailure:Double:OA} we show the open
+automaton computed for the combined architecture of
+Figure~\ref{schema:ArchFailure:BIP:Double}.  It indicates that the two
+timers are forced to be synchronous: each can only tick after the
+other has also started, and then they will tick, reset, and timeout,
+synchronously.
+%
+\hl{This is a very strong assumption, and we are working on a more
 flexible specification (at BIP level) to release this hypothesis while
-keeping the safety properties of the composition.
+keeping the safety properties of the composition.}
+
+\noteInSB{The idea was that, by analysing the combination, we observe
+  that the architecture does not compose well with itself, generating
+  a deadlock (or an implicit deadlock, where only $false$ transitions
+  canb be fired.  Based on this observation, we were to improve it
+  accodingly.  The problem is that I do not see any deadlocks in
+  Figure~\ref{schema:ArchFailure:Double:OA}.  I presume that some of
+  the asterisks should be only $false$ or something of a kind.}
 

### 2019-03-30 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf. paper (minor): removed the mention of priorities)
preuve Th2

--- 2019-03-30 2017-Xudong-SMT/ActaInformatica.tex
@@
 
-\newcommand{\noteSB}[2][color=green!40, size=\tiny]{\todo[#1]{{\bf Simon: } {#2}}}
+\newcommand{\noteSB}[2][color=green!40, size=\tiny]{\todo[#1]{{\bf
+      Note: } {#2}}}
 \newcommand{\noteEM}[2][color=blue!40, size=\tiny]{\todo[#1]{{\bf Eric: } {#2}}}
@@
 
-\input{ActaXFIG/macros.tex}         % Definitions of macros used in XFig figures
+\input{XFIG/macros.tex}         % Definitions of macros used in XFig figures
 \usepackage{macrospNets}
@@
 \begin{example}[Open transitions]
-  Transition $OT_1$ of the pNet $EnableStateCompLeft$ is generated by
+  Transition $OT_2$ of the pNet $EnableStateCompLeft$ is generated by
   combining the first vector of its root node with
-  the second vector of its second node. Its generated predicate is
-  trivially true. The global states show that controler $CState1$ is
+  the second vector of its second node. The global states show that
+  controler $CState1$ is 
   changing from state 0 to 1.
@@
         \begin{mathpar}
-	  OT_1  =
+	  OT_2  =
           \inferrule*[myfraction=\reddottedrule]
@@
         \begin{mathpar}
-	  OT_2  =
+	  OT_2'  =
           \inferrule*[myfraction=\reddottedrule]
@@
 \EndWhile
-\State \QIN{$\mathit{L1}$ = \texttt{filterUnsatTransitions}($\mathit{L,Assignements}$)}
-\State \QIN{$\mathit{OA1}$ = \texttt{makeReachableSubAutomaton}($\mathit{InitState}(P)$,$\mathit{L1}$)}
-\State \Return $\mathit{OA1}$;
+\State $\mathit{L1}$=filterUnsatTransitions($\mathit{L,Assignments}$);
+\State $\mathit{OA_0}$=makeReachableSubAutomaton($\mathit{InitState}(P),L1)$;
+\Repeat $\mathit{OA_n}$=RefineReachableSubAutomaton($\mathit{AO_{n-1}}$)
+\Until  $\mathit{OA_n}=\mathit{OA_{n-1}}$; \Comment Fixpoint reached
+\State \Return $\mathit{OA_n}$;
 
@@
 
-\ERIC{Before the SAT checking step, it may contain symbolic transitions that
+Before the SAT checking step, it may contain symbolic transitions that
 do not have valid ground instanciations. This is not logically
@@
 Then we compute the set of reachable transitions and states to build
-the final open automaton.}
+the final open automaton (more details in section~\ref{section:BuildingTheOpenAutomaton}).
 
@@
 
-%\st{Each of these possible filters is more precise than the previous
-%  ones. But e}
 Even when unification succeeds, it is still possible that
@@
 of the sets of state variables of the individual PLTS states constituting this
-global state. \ERIC{The final assignment sets are assembled when building the
-open automaton from the reachable transitions, see below.}
+global state. The final assignment sets are assembled when building the
+open automaton from the reachable transitions, see below.
 
@@
 Function \texttt{filterUnsatTransitions}, in line 11 of
-Algorithm\ref{alg1} makes use of the Z3 engine to implement the
-satisfiability checking, for all the OTs computed that far, and
-returns the set $L1$ of satisfiable OTs.
+Algorithm\ref{alg1}, and function \\
+\texttt{RefineReachableSubAutomaton}
+in line 13, make use of the Z3 engine to implement the
+satisfiability checking, for all the OTs computed that far.
 
 \subsection{Building the Open Automaton}
-
-\ERIC{The set $L1$ may contain unreachable transitions. To remove those transitions, the last step of the
+\label{section:BuildingTheOpenAutomaton}
+
+The set $L1$ may contain unreachable transitions. To remove those transitions, the last step of the
 algorithm builds the final open automaton via a traversal of $L1$,
@@
 gathered during the traversal using the ``Post'' parts of the
-OTs.}
-
-\ERIC{A further reduction may now be gained by using the information from
+OTs.
+
+A further reduction may now be gained by using the information from
 these sets of possible assignments: adding this information when
@@
 the SAT checking of subsequent transitions. In turn, this may reduce the possible
-assignments of the corresponding target states. In theory, we should
-iterate this procedure, each iteration reducing the set of
+assignments of the corresponding target states. In
+algorithm~\ref{alg1}, we iterate this procedure, each iteration
+reducing the set of 
 transitions and the sets of assignments; the final open automaton
-would be the fixed point of this iteration. In practice, this would be
+is the fixed point of this iteration.
+
+In practice, this could be
 expensive, and it is not incorrect to leave some Unsat OTs in the
 result. From a  practical point of view, very little will be gained to compute the
-fixed point, so we only perform one step of iteration. Further algorithms 
+fixed point, so we would only perform one step of iteration. Further algorithms 
 (e.g. model-checking or equivalence checking) will be able to use the
-full information from the predicates and the assignment sets.}
+full information from the predicates and the assignment sets.
 
@@
 the reachable state space, and assignment sets; this corresponds to
-the set of OTs $L2$ in Algorithm~\ref{alg3}, line 15.
+the automaton $OA_0$ in Algorithm~\ref{alg3}, line 15.
 So the smart algorithm proceeds in two steps: during the
 first step, the SAT checking is done without using any assignment set
-information. Then after the completion of this step, we perform another
-SAT checking of all transitions from step1, using the
-assignment information, in the same way it is done at the end of
-Algorithm~\ref{alg1}.
-
-There is one case much simpler, that is when the pNets contains no
-state variable assignment. Then the set of transitions computed
-on-the-fly is already guaranted to be the final reachable set (line 13).
+information. Then after the completion of this step, we refine the
+reachability computation, using the
+assignment information as described in the previous section.
 
@@
 	\State $\mathit{OTs} = \mathit{MakeTransitions}(P, S)$;
-%%        \State Store $\mathit{OT}$ in $L$; 
 	\For {each $\mathit{OT} \in \mathit{OTs}$}
@@
 \EndWhile
-%%\State Prune the unsatisfiable open transitions in $L$ using the SMT solver;
-\IfThenElse {(NonEmptyAssignmentSet($\mathit{L}$))}
-        {\State \quad\ \Return $\mathit{OA2}$=makeAutomaton($\mathit{InitState}(P),L)$;}
-        {\State \quad\ $\mathit{L2}$=filterUnsatTransitions($\mathit{L,Assignments}$);
-         \State \quad\ \Return $\mathit{OA2}$=makeReachableSubAutomaton($\mathit{InitState}(P),L2)$};
+\State $\mathit{L2}$=filterUnsatTransitions($\mathit{L,Assignments}$);
+\State $\mathit{OA_0}$=makeReachableSubAutomaton($\mathit{InitState}(P),L2)$;
+\Repeat $\mathit{OA_n}$=RefineReachableSubAutomaton($\mathit{AO_{n-1}}$)
+\Until  $\mathit{OA_n}=\mathit{OA_{n-1}}$;
+\State \Return $\mathit{OA_n}$;
+%\EndIf
 \end{algorithmic}  
@@
 with the values of local variables, so we can directly compute the
-reachable part of the automaton using the on-the-fly algorithm.
+reachable part of the automaton using the on-the-fly algorithm (line 13).
 
@@
  $MakeTransitions$ will always returns exactly the same set of OTs, up to
-renaming of these fresh variables
+renaming of these fresh variables. When this is not ambiguous, we will
+speak of equality (of transitions, and of open automata) when we
+should say ``up to renaming of fresh variables''.
 
@@
  \begin{itemize}
-    \item $L1$: the original set of transitions by Algorithm 1
+    \item $L0$: the original set of transitions by Algorithm 1
       (i.e. before line 11), 
@@
     \item $L1_{reach}$: the final set of OTs of Algorithm 1, as computed
-      by line 12.
+      by line 12 (as $AO_0$). Without assignments the following
+      refinement step will do nothing, the fixpoint is already reached.
     \item $L2_{sat}$: the original set of transitions by Algorithm 3
@@
     \item $L2_{reach}$: the final set of OTs of Algorithm 2, as computed
-          by line 13.
+          by line 13. Here also $AO_n = AO_0$.
 \end{itemize}
 
-\paragraph{States:} for each of these, define $States: \langle OT\rangle\rightarrow\langle State\rangle$ which is the function computing the set of target states in a
-set of OTs.
-
-Between two transition sets of the algorithms, define
-$Rename:  L1_{reach} \rightarrow L2_{reach}$ which is the function
-renaming fresh variables.
+\paragraph{States:} for each of these, define
+ $States: \overline{OT}\rightarrow\overline{State}$ the function
+computing the set of target states of a set of OTs. \\
+\noindent
+\emph{Transitions:} between two sets of open transitions computed
+by the algorithms, define $Rename:  L1_{reach} \rightarrow L2_{reach}$
+which is the function renaming fresh variables.
 
@@
 filtering step, so $L1_{sat}=L1_{reach}$ and $L2_{sat}=L2_{reach}$.
-
-According to the definition of global states in
-page~\pageref{def-states}, the global state
-$\ostate{\tilde{s}}=\ostate{\tilde{s_0...s_n}}$ is a composition of $n$
-pLTS states $s_{i}^{i\in [0,n]}$.
-
-From the structure of the main loop of the algorithms, we can get that algorithm~\ref{alg1} computes less transitions than algorithm~\ref{alg3}, i.e.
-$L2_{reach}\subseteq  L1$, and as a consequence $States(L2_{reach})\subseteq  States(L1)$, so we have:
-\[\forall \ostate{\tilde{u}}\in States(L2_{reach}), \exists\ostate{\tilde{t}}\in States(L1), \ostate{\tilde{t}}=\ostate{\tilde{a_0...a_n}}=\ostate{\tilde{u}}.\]
-
-The reachability function $computeReachableSubAutomaton$ being called
-with the same initial state $\ostate{\tilde{t_0}}$, this state is the
-initial state of both $L1_{reach}$ and $L2_{reach}$.
-
-%  If there is an initial state $\ostate{\tilde{t_0}}\in States(L2_{reach})$ then the initial state of the original automaton $\ostate{\tilde{t_0}}\in States(L1_{reach})$ must exists.
-
-\noteInEM{What you are doing below is a proof by recursion on the
-  length of the path reaching a given OT, isn't it ? I suggest you
-  explicite this and conclude $L2_{reach}\subseteq  L1_{reach}$.}
-
-Suppose that  $\ostate{\tilde{t}}\in States(L2_{reach})$. It is reachable in the result automaton of Algorithm 3, so there exists a sequence of transitions 
-\[\ostate{\tilde{t_0}}\xrightarrow{l_1}\ostate{\tilde{t_1}}\xrightarrow{l_2}...\xrightarrow{l_{n}}\ostate{\tilde{t}}\] where in each label of the transition $Pred_{l_i}^{i\in [1,n]}$ is satisfiable.
-For the same state $\ostate{\tilde{t}}\in States(L1_{reach})$, there exists a sequence of transitions \[\ostate{\tilde{t_0}}\xrightarrow{l'_1}\ostate{\tilde{t_1}}\xrightarrow{l'_2}...\xrightarrow{l'_{n}}\ostate{\tilde{t}}\]where for each transition $Rename(\ostate{\tilde{t_{i-1}}}\xrightarrow{l_{i}}\ostate{\tilde{t_{i}}}) = \ostate{\tilde{t_{i-1}}}\xrightarrow{l'_{i}}\ostate{\tilde{t_{i}}}$ and $Pred_{l'_i}^{i\in [1,n]}$ is satisfiable.
-From the structure of the algorithms, 
-\[\forall \ostate{\tilde{t}}\in States(L2_{reach}), \ostate{\tilde{t}}\xrightarrow{l'_{n+1}}\ostate{\tilde{t'}}\in L2_{reach}\]
-\[\exists \ostate{\tilde{t}}\xrightarrow{l_{n+1}}\ostate{\tilde{t'}}\in L1 \quad s.t.\quad Rename(\ostate{\tilde{t}}\xrightarrow{l_{n+1}}\ostate{\tilde{t'}}) = \ostate{\tilde{t}}\xrightarrow{l'_{n+1}}\ostate{\tilde{t'}})\]
-where $Pred_{l_{n+1}}$ and $Pred_{l'_{n+1}}$ are satisfiable.
-
-Then we can get a new longer sequence \[\ostate{\tilde{t_0}}\xrightarrow{l_1}\ostate{\tilde{t_1}}\xrightarrow{l_2}...\xrightarrow{l_{n}}\ostate{\tilde{t}}\xrightarrow{l_{n+1}}\ostate{\tilde{t}}\] \[\Rightarrow\ostate{\tilde{t'}}\in States(L1_{reach})\wedge\ostate{\tilde{t}}\xrightarrow{l_{n+1}}\ostate{\tilde{t'}}\in L1_{reach}\in L1.\] So for arbitrary transition in $L2_{reach}$, there is a same transition in $L1_{reach}$ after renaming its label, then we get
-$L2_{reach}\subseteq  L1_{reach}$.
-
-Conversely,
-\[\forall \ostate{\tilde{t'}}\notin States(L2_{reach}), \ostate{\tilde{t}}\xrightarrow{l'}\ostate{\tilde{t'}}\notin L2_{reach},\quad\exists \ostate{\tilde{t'}}\in States(L1), \ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L1\]
-where $Pred_{l}$ and $Pred_{l'}$ are not satisfiable.
-As pruning function in Algorithm 1 will remove all the unsatisfiable transitions, then $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\notin L1_{reach}$.
-
-As a result, we get that $L1_{reach}=L2_{reach}$, and subsequently, $States(L1_{reach})=States(L2_{reach})$.
+We want to prove that $L1_{reach}=L2_{reach}$, that will imply
+the equality of the 2 open automata.
+
+\medskip
+Let $S=\ostate{\overline{s}}=\ostate{\{s_{i}\}^{i\in Leaves(pn)}}$
+range over the global states $States(L0)$, 
+The only difference between the main loops of the algorithms is that 
+algorithm~\ref{alg3} only retains the satisfiable OTs (line 6-7), so 
+algorithm~\ref{alg3} computes less transitions than
+algorithm~\ref{alg1}. Formaly $L2_{reach}\subseteq  L2_{sat} \subseteq L0$, and as a consequence $States(L2_{reach})\subseteq  States(L0)$, so we have:\\
+\centerline{$\forall \ostate{\overline{u}}\in States(L2_{reach}), \exists\ostate{\overline{t}}\in States(L0), \ostate{\overline{t}}=\ostate{\overline{u}}$}
+
+For a global state $S$, and a set of OTs $L$, define its distance
+$|S|_L$ as the length $n$ of (one of the) shortest chain
+$S_0\xrightarrow{l_1}S_1\xrightarrow{l_2}...S_{n-1}\xrightarrow{l_{n}}S$
+  from the initial state $S_0$, with $\forall k\in [1..n], l_k \in L$.
+
+\medskip
+We will prove by induction on the distance from the original state,
+that $\forall S \in L0. S \in States(L2_{reach}) \land |S|_{l2_{reach}}=n => S
+\in States(L1_{reach})$, and vice-versa.
+
+  The initial property is trivial, for $n=0$, both state sets of
+  distance zero are reduced to $S_0$.
+
+  Suppose our property is true for distance $n$, and
+  suppose $|S|_{L2_{reach}}=n+1$, then there exist a chain
+  $S_0\xrightarrow{l_1}S_1\xrightarrow{l_2}...S_{n}\xrightarrow{l_{n+1}}S$
+  with all $l_k \in L2_{reach}$. In particular, as
+  $L2_{reach}\subseteq L2_{sat}$, $l_{n+1} \in L2_{sat}$, meaning it
+  it's predicate is satisfiable.
+
+  By induction hypothesis, we get $S_{n} \in States(L1_{reach})$, so during the
+  call of $makeReachableSubAutomaton$ in algorithm~\ref{alg1}, line 12, the OT
+  $S_n \xrightarrow{l_{n}}S$ will be check and found SAT, so
+  $S \in States(L1_{reach})$.
+
+  Conversely if $|S|_{L1_{reach}}=n+1$, we get a similar chain, in
+  $L1_{reach}$, with $S_n \xrightarrow{l_{n}}S, S_n \in
+  States(L1_{reach})$, and $l_n$ satisfiable. By induction, we have
+  $S_n \in States(L2_{reach})=States(L2_{sat})$, so $l_n$ will have
+  been checked ``on-the-fly'', in line 6 of algorithm~\ref{alg3}, and
+  the OT $S_n \xrightarrow{l_{n}}S$ added to $L2_{sat})$, and we
+  conclude $S \in States(L2_{reach})$.
+
+Remember that $L0$ is finite, so we conclude $L1_{reach}=L2_{reach}$, and $States(L1_{reach})=States(L2_{reach})$.
+
+%  If there is an initial state $\ostate{\overline{t_0}}\in States(L2_{reach})$ then the initial state of the original automaton $\ostate{\overline{t_0}}\in States(L1_{reach})$ must exists.
+
+%% \noteInEM{What you are doing below is a proof by recursion on the
+%%   length of the path reaching a given OT, isn't it ? I suggest you
+%%   explicite this and conclude $L2_{reach}\subseteq  L1_{reach}$.}
+
+%% Suppose that  $\ostate{\overline{t}}\in States(L2_{reach})$. It is reachable in the result automaton of Algorithm 3, so there exists a sequence of transitions 
+%% \[\ostate{\overline{t_0}}\xrightarrow{l_1}\ostate{\overline{t_1}}\xrightarrow{l_2}...\xrightarrow{l_{n}}\ostate{\overline{t}}\] where in each label of the transition $Pred_{l_i}^{i\in [1,n]}$ is satisfiable.
+For the same state $\ostate{\overline{t}}\in States(L1_{reach})$, there exists a sequence of transitions \[\ostate{\overline{t_0}}\xrightarrow{l'_1}\ostate{\overline{t_1}}\xrightarrow{l'_2}...\xrightarrow{l'_{n}}\ostate{\overline{t}}\]where for each transition $Rename(\ostate{\overline{t_{i-1}}}\xrightarrow{l_{i}}\ostate{\overline{t_{i}}}) = \ostate{\overline{t_{i-1}}}\xrightarrow{l'_{i}}\ostate{\overline{t_{i}}}$ and $Pred_{l'_i}^{i\in [1,n]}$ is satisfiable.
+%% From the structure of the algorithms, 
+%% \[\forall \ostate{\overline{t}}\in States(L2_{reach}), \ostate{\overline{t}}\xrightarrow{l'_{n+1}}\ostate{\overline{t'}}\in L2_{reach}\]
+%% \[\exists \ostate{\overline{t}}\xrightarrow{l_{n+1}}\ostate{\overline{t'}}\in L1 \quad s.t.\quad Rename(\ostate{\overline{t}}\xrightarrow{l_{n+1}}\ostate{\overline{t'}}) = \ostate{\overline{t}}\xrightarrow{l'_{n+1}}\ostate{\overline{t'}})\]
+%% where $Pred_{l_{n+1}}$ and $Pred_{l'_{n+1}}$ are satisfiable.
+
+%% Then we can get a new longer sequence \[\ostate{\overline{t_0}}\xrightarrow{l_1}\ostate{\overline{t_1}}\xrightarrow{l_2}...\xrightarrow{l_{n}}\ostate{\overline{t}}\xrightarrow{l_{n+1}}\ostate{\overline{t}}\] \[\Rightarrow\ostate{\overline{t'}}\in States(L1_{reach})\wedge\ostate{\overline{t}}\xrightarrow{l_{n+1}}\ostate{\overline{t'}}\in L1_{reach}\in L1.\] So for arbitrary transition in $L2_{reach}$, there is a same transition in $L1_{reach}$ after renaming its label, then we get
+%% $L2_{reach}\subseteq  L1_{reach}$.
+
+%% Conversely,
+%% \[\forall \ostate{\overline{t'}}\notin States(L2_{reach}), \ostate{\overline{t}}\xrightarrow{l'}\ostate{\overline{t'}}\notin L2_{reach},\quad\exists \ostate{\overline{t'}}\in States(L1), \ostate{\overline{t}}\xrightarrow{l}\ostate{\overline{t'}}\in L1\]
+%% where $Pred_{l}$ and $Pred_{l'}$ are not satisfiable.
+As pruning function in Algorithm 1 will remove all the unsatisfiable transitions, then $\ostate{\overline{t}}\xrightarrow{l}\ostate{\overline{t'}}\notin L1_{reach}$.
+
+%As a result, we get that $L1_{reach}=L2_{reach}$, 
 %We will construct a mapping $f$: $State(L1-reach)\rightarrow
@@
 %\setlength{\itemindent}{3.5em}
-%	\item[(Surjective)] If $\ostate{\tilde{s_0}}=Initial(p)$ then $f(\ostate{\tilde{s}})=\ostate{\tilde{t_0}}=Initial(p)$ must exists, the transitions started from them fulfill that
+%	\item[(Surjective)] If $\ostate{\overline{s_0}}=Initial(p)$ then $f(\ostate{\tilde{s}})=\ostate{\tilde{t_0}}=Initial(p)$ must exists, the transitions started from them fulfill that
 %	\[\forall \ostate{\tilde{t_0'}}, \ostate{\tilde{t_0}}\xrightarrow{v_j}\ostate{\tilde{t_0'}}\in L_{Smart},\quad \exists\ostate{\tilde{s'}},\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}\in L.\]
@@
 
+\paragraph{General case with assignments.}
 But in the presence of assignments, we need to collect all of them
@@
 Figure~\ref{schema:enable-OAs}.
-\noteSB{I guess pNets in this figure have to be replaced by open
-  automata}
 Note that although these automata look very similar to the PLTS
@@
 Figure~\ref{schema:enable-composed}. Its open automaton is shown in
-Figure~\ref{schema:enable3bis}. Building the symmetric system \noteSB{Should this be typeset in math mode?}``(P>>Q)>>R'' in a similar
+Figure~\ref{schema:enable3bis}. Building the symmetric system ``(P>>Q)>>R'' in a similar
 way will allow us to prove that they are bisimilar (the Enable
@@
 
-\subsection{BIP Failure Monitor Architecture}
+\subsection{BIP FailureTimer Architecture}
 \label{section:FailureTimer}
@@
 
-In this section, we present the Failure Monitor architecture from the
+As a running example we use the Failure Monitor architecture from the
 CubETH nanosatellite on-board software
@@
 Failure Monitor architecture used in~\cite{CubETH-case-study}.
-%
-The architecture consists of 2 \emph{coordinator components}
-($\NameCtrl$ and $\NameTimer$, for \emph{Control} and \emph{Timer},
-respectively), 5 \emph{dangling ports} ($\PortFail$, $\PortResume$,
-$\PortTick$, $\PortReset$ and $\PortAsk$) and 5 connectors.
-%
-%% Contrary to standard BIP models, architectures comprise one or several
-%% \emph{operand} components, whereof only the set of \emph{ports} is
-%% given.  Here, the operand component is $\NameOprnd$ and its interface
-%% consists of the ports $\PortResume$ and $\PortFail$.
-%% The two \emph{coordinator} components\mdash $\NameCtrl$ and
-%% $\NameTimer$\mdash are standard
-The  \emph{behaviour} of BIP components %% insofar as they also
-%% have their 
-is specified by finite automata extended with
+Contrary to standard BIP models, architectures comprise one or several
+\emph{operand} components, whereof only the set of \emph{ports} is
+given.  Here, the operand component is $\NameOprnd$ and its interface
+consists of the ports $\PortResume$ and $\PortFail$.
+The two \emph{coordinator} components\mdash $\NameCtrl$ and
+$\NameTimer$\mdash are standard BIP components insofar as they also
+have their \emph{behaviour} specified by finite automata extended with
 local data variables.  Transitions of these automata are labelled with
 the ports of the corresponding components, Boolean guards and update
-functions on local variables.  %% For instance, the loop transition
-%% $t_1 \goesto{\PortTick, [t < Max], t:=t+1} t_1$
-%% in the $\NameTimer$ component is labelled by the port $\PortTick$. It
-%% can be fired only when the current value of the local variable $t$ is
-%% lower than $Max$.  Upon firing, this transition increments the value
-%% of $t$ by $1$.  When omitted, the default guard (\resp update
-%% function) is the constant predicate $\true$ (\resp the $\mathit{skip}$
-%% operator).  The constant $\mathrm{Max}$ above, is a parameter of the
-%% architecture.
-
-%% Connectors are hierarchical, tree-like structures with component ports
-%% at the leaves.  They define sets of \emph{interactions}, 
-Based on the
-attributes of the connected ports, which may be
+functions on local variables.  For instance, the loop transition
+$t_1 \goesto{\PortTick, [t < Max], t:=t+1} t_1$
+in the $\NameTimer$ component is labelled by the port $\PortTick$. It
+can be fired only when the current value of the local variable $t$ is
+lower than $Max$.  Upon firing, this transition increments the value
+of $t$ by $1$.  When omitted, the default guard (\resp update
+function) is the constant predicate $\true$ (\resp the $\mathit{skip}$
+operator).  The constant $\mathrm{Max}$ above, is a parameter of the
+architecture.
+
+Connectors are hierarchical, tree-like structures with component ports
+at the leaves.  They define sets of \emph{interactions}, based on the
+attributes of the connected ports~\cite{BliSif08-acp-tc}, which may be
 either \emph{triggers} (triangles in Figure~\ref{schema:ArchFailure:BIP})
-or \emph{synchrons} (bullets in Figure~\ref{schema:ArchFailure:BIP}),
+or \emph{synchrons} (bullets in Figure~\ref{schema:ArchFailure:BIP}).
 %
-connectors specify the syncrhonisations (also called
-\emph{interactions}) between the transitions of the individual
-components.  Intuitively, triggers can initiate interactions, whereas
-synchrons can only join.  If a connector does not have triggers, all
-the involved ports must synchronise~\cite{BliSif08-acp-tc}.
-%% %
-%% If all the sub-connectors of a connector are synchrons, then an
-%% interaction may be executed by the connector only if each subconnector
-%% can contribute.
-%% %
-%% If at least one of the sub-connectors is a trigger, then any
-%% interaction consisting of contributions of any set of sub-connectors,
-%% \emph{involving at least one of the triggers}, can be executed.
+If all the sub-connectors of a connector are synchrons, then an
+interaction may be executed by the connector only if each subconnector
+can contribute.
+%
+If at least one of the sub-connectors is a trigger, then any
+interaction consisting of contributions of any set of sub-connectors,
+\emph{involving at least one of the triggers}, can be executed.
 %
@@
 particular, this means that whenever the transition 
-$\cstate{0} \goesto{\PortFail} \cstate{1}$ is fired, so is the transition
-$\tstate{0} \goesto{\PortStart, t:=0} \tstate{1}$,
+$c_0 \goesto{\PortFail} c_1$ is fired, so is the transition
+$t_0 \goesto{\PortStart, t:=0} t_1$,
 initialising the timer.  The binary connector $\NameTimer.\PortStart
 \bullet\!\!\!-\!\!\!-\!\!\!\bullet \NameCtrl.\PortFail$ is a
-sub-connector of a hierarchical connector, where the dangling port
+sub-connector of a hierarchical connector, where the port
 $\NameOprnd.\PortFail$ is a trigger.  Thus, the above interaction can
@@
 
-\hl{Application of the Failure Monitor architecture ensures that, whenever
+Application of the Failure Monitor architecture ensures that, whenever
 a failure is registered in the operand component, the system will be
 reset, unless a resumption is registered within $\mathrm{Max}$ time
-units (more details in Section~\ref{section:FailureTimer}).}
+units (more details in Secion~\ref{section:FailureTimer}).
 
@@
 above Failure Monitor architecture.  This encoding is structural: each
-coordinator component is encoded as a PLTS; dangling ports are encoded as actions of the hole;
-%%  and the operand component as a hole;
-connectors of the BIP model are encoded as synchronisation vectors.
-Each connector that does not involve triggers is trivially encoded by
-a synchronisation vector comprising the same ports ($SV2$, $SV3$ and
-$SV4$).  In order to encode the semantics of the connectors involving
-triggers, we use the classical approach where non-participation of a
-port in an interaction is simulated by an additional loop
-transition~\cite{milner83-calculi}.  To this end, we consider an
-action algebra involving additional Boolean variables: the effective
-transitions carry the value $\true$ (\eg $\cstate{0}
-\goesto{\PortFail(\true)} \cstate{1}$), whereas the added loops carry
-the value $\false$ (\eg $\cstate{2} \goesto{\PortFail(\false)}
-\cstate{2}$).  In the synchronisation vectors, we use these variables
-to encode the connector structure as a Boolean predicate.  For
-example, $SV0$ encodes the connector discussed above: the predicate
-$(b1=b2) \land (b1\lor b2 \Rightarrow b0)$ means that the ``true''
-transitions $\NameCtrl.\PortFail$ and $\NameTimer.\PortStart$ can only
-fire together ($b1 = b2$) and whenever one of them fires,
+coordinator component is encoded as a PLTS and the operand
+component as a hole; connectors of the BIP model are encoded as
+synchronisation vectors.  Each connector that does not involve
+triggers is trivially encoded by a synchronisation vector comprising
+the same ports.  In order to encode the semantics of the connectors
+involving triggers, we 1)~in the PLTS encoding the coordinator
+components, add loop transitions to ensure that all ports involved in
+such connectors are enabled in all states, 2)~associate a Boolean
+value to each of these ports: the original transitions carry the value
+$\true$ (\eg $c_0 \goesto{\PortFail(\true)} c_1$) and the
+added loops carry the value $\false$ (\eg $c_2
+\goesto{\PortFail(\false)} c_2$), 3)~add to the corresponding
+synchronisation vectors the Boolean predicate encoding the connector
+structure.  For example, $SV0$ encodes the connector discussed above:
+the predicate $(b1=b2) \land (b1\lor b2 \Rightarrow b0)$ means that the
+``true'' transitions $\NameCtrl.\PortFail$ and $\NameTimer.\PortStart$
+can only fire together ($b1 = b2$) and whenever one of them fires,
 $\NameOprnd.\PortFail$ must fire also ($b1 \lor b2 \Rightarrow b0$).
@@
 %
-\noteEM{Decide later if this is still useful}Although, for the sake of
-brevity, we omit priorities from the encoding, this can be easily
-achieved, by introducing another set of additional Boolean variables
-for relevant ports~\cite{BarBliu15-offer-scico}.
+\noteEM{Decide later if this is still useful}Although, for the sake of brevity, we omit priorities from the
+encoding, this can be easily achieved, by introducing additional
+Boolean variables for relevant ports~\cite{BarBliu15-offer-scico}.
 

### 2019-03-30 2017-Xudong-SMT/ActaInformatica.tex

@@
 
-\input{XFIG/macros.tex}         % Definitions of macros used in XFig figures
+\input{ActaXFIG/macros.tex}         % Definitions of macros used in XFig figures
 \usepackage{macrospNets}
@@
   \caption{The two open automata}
-  %% \noteSB{I guess pNets in this figure have to be replaced by open
-  %%   automata}
   \label{schema:enable-OAs}
@@
 Failure Monitor architecture used in~\cite{CubETH-case-study}.
-Contrary to standard BIP models, architectures comprise one or several
-\emph{operand} components, whereof only the set of \emph{ports} is
-given.  Here, the operand component is $\NameOprnd$ and its interface
-consists of the ports $\PortResume$ and $\PortFail$.
-The two \emph{coordinator} components\mdash $\NameCtrl$ and
-$\NameTimer$\mdash are standard BIP components insofar as they also
-have their \emph{behaviour} specified by finite automata extended with
+%
+The architecture consists of 2 \emph{coordinator components}
+($\NameCtrl$ and $\NameTimer$, for \emph{Control} and \emph{Timer},
+respectively), 5 \emph{dangling ports} ($\PortFail$, $\PortResume$,
+$\PortTick$, $\PortReset$ and $\PortAsk$) and 5 connectors.
+%
+%% Contrary to standard BIP models, architectures comprise one or several
+%% \emph{operand} components, whereof only the set of \emph{ports} is
+%% given.  Here, the operand component is $\NameOprnd$ and its interface
+%% consists of the ports $\PortResume$ and $\PortFail$.
+%% The two \emph{coordinator} components\mdash $\NameCtrl$ and
+%% $\NameTimer$\mdash are standard
+The  \emph{behaviour} of BIP components %% insofar as they also
+%% have their 
+is specified by finite automata extended with
 local data variables.  Transitions of these automata are labelled with
 the ports of the corresponding components, Boolean guards and update
-functions on local variables.  For instance, the loop transition
-$t_1 \goesto{\PortTick, [t < Max], t:=t+1} t_1$
-in the $\NameTimer$ component is labelled by the port $\PortTick$. It
-can be fired only when the current value of the local variable $t$ is
-lower than $Max$.  Upon firing, this transition increments the value
-of $t$ by $1$.  When omitted, the default guard (\resp update
-function) is the constant predicate $\true$ (\resp the $\mathit{skip}$
-operator).  The constant $\mathrm{Max}$ above, is a parameter of the
-architecture.
-
-Connectors are hierarchical, tree-like structures with component ports
-at the leaves.  They define sets of \emph{interactions}, based on the
-attributes of the connected ports~\cite{BliSif08-acp-tc}, which may be
+functions on local variables.  %% For instance, the loop transition
+%% $t_1 \goesto{\PortTick, [t < Max], t:=t+1} t_1$
+%% in the $\NameTimer$ component is labelled by the port $\PortTick$. It
+%% can be fired only when the current value of the local variable $t$ is
+%% lower than $Max$.  Upon firing, this transition increments the value
+%% of $t$ by $1$.  When omitted, the default guard (\resp update
+%% function) is the constant predicate $\true$ (\resp the $\mathit{skip}$
+%% operator).  The constant $\mathrm{Max}$ above, is a parameter of the
+%% architecture.
+Although this is not visible in the figure, below we will assume that
+the dangling ports $\PortFail$ and $\PortResume$ belong to the operand
+component, whereas the dangling ports $\PortTick$, $\PortAsk$ and
+$\PortReset$ represent actions of the environment.
+
+%% Connectors are hierarchical, tree-like structures with component ports
+%% at the leaves.  They define sets of \emph{interactions}, 
+Based on the
+attributes of the connected ports, which may be
 either \emph{triggers} (triangles in Figure~\ref{schema:ArchFailure:BIP})
-or \emph{synchrons} (bullets in Figure~\ref{schema:ArchFailure:BIP}).
+or \emph{synchrons} (bullets in Figure~\ref{schema:ArchFailure:BIP}),
 %
-If all the sub-connectors of a connector are synchrons, then an
-interaction may be executed by the connector only if each subconnector
-can contribute.
-%
-If at least one of the sub-connectors is a trigger, then any
-interaction consisting of contributions of any set of sub-connectors,
-\emph{involving at least one of the triggers}, can be executed.
+connectors specify the syncrhonisations (also called
+\emph{interactions}) between the transitions of the individual
+components.  Intuitively, triggers can initiate interactions, whereas
+synchrons can only join.  If a connector does not have triggers, all
+the involved ports must synchronise~\cite{BliSif08-acp-tc}.
+%% %
+%% If all the sub-connectors of a connector are synchrons, then an
+%% interaction may be executed by the connector only if each subconnector
+%% can contribute.
+%% %
+%% If at least one of the sub-connectors is a trigger, then any
+%% interaction consisting of contributions of any set of sub-connectors,
+%% \emph{involving at least one of the triggers}, can be executed.
 %
@@
 
-Application of the Failure Monitor architecture ensures that, whenever
-a failure is registered in the operand component, the system will be
-reset, unless a resumption is registered within $\mathrm{Max}$ time
-units (more details in Secion~\ref{section:FailureTimer}).
+Intuitively, application of the Failure Monitor architecture ensures
+that, whenever a failure is registered in the operand component, the
+system will be reset, unless a resumption is registered within
+$\mathrm{Max}$ time units.  Formally, this statement is decomposed
+into several properties, among which 
+%
+1)~the safety property \emph{``There is always a possibility to reset
+  the system after a single failure''} (\ie without additional
+failures having to occur in the meantime) specified using CTL as
+%
+\begin{equation}
+  \label{eq:FM:safety}
+  \AG
+  \bigl(\PortFail \rightarrow
+  \EX \EU[]{\lnot \PortFail}{\PortReset}\bigr)
+\end{equation}
+%
+and 2)~the liveness property \emph{``a reset will be fired when asked
+  for by a timeout''}:
+%
+\begin{equation}
+  \label{eq:FM:liveness}
+  \mathtt{AG}(\PortAsk \rightarrow \mathtt{AF}\ \PortReset).
+\end{equation}
+%
+Additional properties are provided in~\cite{Avocs-RR}.
+
+%% \TODO{it would be good to express here maybe 2 properties of the
+%%   architecture, maybe one taken from the original study, and another
+%%   one involving the timer data (number of ticks ?)}
 
@@
 above Failure Monitor architecture.  This encoding is structural: each
-coordinator component is encoded as a PLTS and the operand
-component as a hole; connectors of the BIP model are encoded as
-synchronisation vectors.  Each connector that does not involve
-triggers is trivially encoded by a synchronisation vector comprising
-the same ports.  In order to encode the semantics of the connectors
-involving triggers, we 1)~in the PLTS encoding the coordinator
-components, add loop transitions to ensure that all ports involved in
-such connectors are enabled in all states, 2)~associate a Boolean
-value to each of these ports: the original transitions carry the value
-$\true$ (\eg $c_0 \goesto{\PortFail(\true)} c_1$) and the
-added loops carry the value $\false$ (\eg $c_2
-\goesto{\PortFail(\false)} c_2$), 3)~add to the corresponding
-synchronisation vectors the Boolean predicate encoding the connector
-structure.  For example, $SV0$ encodes the connector discussed above:
-the predicate $(b1=b2) \land (b1\lor b2 \Rightarrow b0)$ means that the
-``true'' transitions $\NameCtrl.\PortFail$ and $\NameTimer.\PortStart$
-can only fire together ($b1 = b2$) and whenever one of them fires,
+coordinator component is encoded as a PLTS; dangling ports belonging
+to the operand component are encoded as actions of the hole; 
+%%  and the operand component as a hole;
+connectors of the BIP model are encoded as synchronisation vectors,
+\noteSB{Eric, please check whether this is ok.}\hl{with ports
+  representing the actions of the environment used as global actions}.
+Each connector that does not involve triggers is trivially encoded by
+a synchronisation vector comprising the same ports ($SV2$, $SV3$ and
+$SV4$).  In order to encode the semantics of the connectors involving
+triggers, we use (in $SV0$ and $SV1$) the classical approach where
+non-participation of a port in an interaction is simulated by an
+additional loop transition~\cite{milner83-calculi}.  To this end, we
+consider an action algebra involving additional Boolean variables: the
+effective transitions carry the value $\true$ (\eg $\cstate{0}
+\goesto{\PortFail(\true)} \cstate{1}$), whereas the added loops carry
+the value $\false$ (\eg $\cstate{2} \goesto{\PortFail(\false)}
+\cstate{2}$).  In the synchronisation vectors, we use these variables
+to encode the connector structure as a Boolean predicate.  For
+example, $SV0$ encodes the connector discussed above: the predicate
+$(b1=b2) \land (b1\lor b2 \Rightarrow b0)$ means that the ``true''
+transitions $\NameCtrl.\PortFail$ and $\NameTimer.\PortStart$ can only
+fire together ($b1 = b2$) and whenever one of them fires,
 $\NameOprnd.\PortFail$ must fire also ($b1 \lor b2 \Rightarrow b0$).
@@
 %
-\noteEM{Decide later if this is still useful}Although, for the sake of brevity, we omit priorities from the
-encoding, this can be easily achieved, by introducing additional
-Boolean variables for relevant ports~\cite{BarBliu15-offer-scico}.
+%% \noteEM{Decide later if this is still useful}Although, for the sake of
+%% brevity, we omit priorities from the encoding, this can be easily
+%% achieved, by introducing another set of additional Boolean variables
+%% for relevant ports~\cite{BarBliu15-offer-scico}.
 

### 2019-03-30 2017-Xudong-SMT/ActaInformatica.tex
merge proof2 and simon

@@
 
-When the pNets contains no assignment, there is no need for the last
-filtering step, so $L1_{sat}=L1_{reach}$ and $L2_{sat}=L2_{reach}$.
+%% When the pNets contains no assignment, there is no need for the last
+%% filtering step, so $L1_{sat}=L1_{reach}$ and $L2_{sat}=L2_{reach}$.
 We want to prove that $L1_{reach}=L2_{reach}$, that will imply
@@
 
-\medskip
+\smallskip
 Let $S=\ostate{\overline{s}}=\ostate{\{s_{i}\}^{i\in Leaves(pn)}}$
@@
 We will prove by induction on the distance from the original state,
-that $\forall S \in L0. S \in States(L2_{reach}) \land |S|_{l2_{reach}}=n => S
+that $\forall S \in L0. \forall n \in \mathbb{N}. S \in States(L2_{reach}) \land |S|_{l2_{reach}}=n => S
 \in States(L1_{reach})$, and vice-versa.
@@
   The initial property is trivial, for $n=0$, both state sets of
-  distance zero are reduced to $S_0$.
+  distance zero are reduced to $\{S_0\}$.
 
@@
   with all $l_k \in L2_{reach}$. In particular, as
-  $L2_{reach}\subseteq L2_{sat}$, $l_{n+1} \in L2_{sat}$, meaning it
+  $L2_{reach}\subseteq L2_{sat}$, $l_{n+1} \in L2_{sat}$, meaning 
   it's predicate is satisfiable.
@@
   $S_n \in States(L2_{reach})=States(L2_{sat})$, so $l_n$ will have
-  been checked ``on-the-fly'', in line 6 of algorithm~\ref{alg3}, and
-  the OT $S_n \xrightarrow{l_{n}}S$ added to $L2_{sat})$, and we
+  been checked ``on-the-fly'', in line 6 of algorithm~\ref{alg3},
+  the OT $S_n \xrightarrow{l_{n}}S$ added to $L2_{sat}$, and we
   conclude $S \in States(L2_{reach})$.
 
-Remember that $L0$ is finite, so we conclude $L1_{reach}=L2_{reach}$, and $States(L1_{reach})=States(L2_{reach})$.
+Remember $L0$ is finite, so we conclude $L1_{reach}=L2_{reach}$, and $States(L1_{reach})=States(L2_{reach})$.
 
@@
 \paragraph{General case with assignments.}
-But in the presence of assignments, we need to collect all of them
+In the presence of assignments, we need to collect all of them
   before using the assignment information to refine the SAT
   checking. Still, the smart strategy will explore a reduced state
-  space, not necessarily the minimal one (discussion later). In the
-  following theorem, both algorithm are considered in their complete
+  space, not necessarily the minimal one. In the
+  following theorem, both algorithms are considered in their complete
   version, meaning the reachability (with assignments) step is
@@
 \begin{proof}
-In Theorem 2, we have already proved that the result automata $OA_1$ and $OA_2$ of two algorithms are the same if the pNet contains no assignment to its state variables.
-
-We define the function $States$ as before, and the function $Assignments : \langle OT\rangle\times State\rightarrow\langle Assign\rangle$
+  Define the OT sets $L0, L1_{sat}, L2_{sat}, L2_{reach}$ as previously, and:
+
+  \begin{itemize}
+    \item $L1_{reach*}$ = final set of OTs of Algorithm 1, as computed
+        by an iterative application of makeReachableSubAutomaton (line
+        14) up to fixpoint.
+      \item $L2_{reach*}$ = final set of OTs of Algorithm 2, as computed
+        by an iterative application of makeReachableSubAutomaton (line
+        16) up to fixpoint.
+  \end{itemize}
+
+?? In Theorem 2, we have already proved that the result automata $OA_1$ and $OA_2$ of two algorithms are the same if the pNet contains no assignment to its state variables.
+
+We define the function $States$ as before, and the function $Assignments : \overline{OT}\ \times State\rightarrow \overline{Assign}$
 computing the set of assignments of a global state from a given set of OTs.
 
-The structure implicitly computed by the algorithm is a triple $ Aut= \langle OTs, States,\\ Assigns\rangle$.
-
-Then the assignments set of $OA_1$ is $\{Assignments(L1, State_{i})\}^{State_{i}\in States(L1)}$ and $OA_2$ is $\{Assignments(L2_{sat}, State_{j})\}^{State_{j}\in States(L2_{sat})}$.
-The result triples should be
-\[Aut_1 = \langle L1_{sat}, States(L1_{sat}), \{Assignments(L1, State_{i})\}^{State_{i}\in States(L1)}\rangle\] and \[Aut_2 = \langle L2_{sat}, States(L2_{sat}), \{Assignments(L2_{sat}, State_{j})\}^{State_{j}\in States(L2_{sat})}\rangle \ .
-\]
-
-Basing on the notation of the triple, we define the function $Refine : Aut \rightarrow Aut$ implementing $makeReachableSubAutomaton(S0,OTs)$, it uses the assignments of the previous step to refine the computed reachable space.
+The structure implicitly computed by both algorithms is a triple $ Aut= \langle \overline{OT}, \overline{State},\\ \overline{Assign}\rangle$.
+
+Then the assignments set of $OA_1$ is $\{Assignments(L1, S_i)\}^{S_i\in States(L1)}$ and $OA_2$ is $\{Assignments(L2_{sat}, S_j)\}^{S_j\in States(L2_{sat})}$. The result triples are:  
+\noindent
 \begin{align*}
-Refine(Aut) &=\langle L', States(L'), \{Assignments(L', State_{i})\}^{State_{i}\in States(L')}\rangle \\
+Aut_1 = \langle L1_{sat}, States(L1_{sat}), \{Assignments(L1, S_i)\}^{S_i\in States(L1)}\rangle\\
+Aut_2 = \langle L2_{sat}, States(L2_{sat}), \{Assignments(L2_{sat}, S_j)\}^{S_j\in States(L2_{sat})}\rangle \ 
+\end{align*}
+
+Based on this triple structure, we define the function $Refine : Aut \rightarrow Aut$ modeling $makeReachableSubAutomaton(S0,OTs)$.
+It uses the assignments of the previous step to refine the computed reachable space:
+\begin{align*}
+Refine(Aut) &=\langle L', States(L'), \{Assignments(L', S_i)\}^{S_i\in States(L')}\rangle \\
 &=Aut'
 \end{align*}
-where $L' = L - L_{unsat}$, $L_{unsat}$ is the set of unsatisfiable transitions checked in this iteration.
-So there must have $|L'|<|L|$, and potentially, their target states and corresponding assignments could be reduced:
-\[States_{L'}=\{State_{init}\}\cup \bigcup States(L'),\]
+where $L' = L - L_{unsat}$, and $L_{unsat}$ is the set of unsatisfiable transitions checked in this iteration.
+We have $L'\subseteq L$, and potentially, their target states and corresponding assignments may be reduced:
+\[States(L')=\{S_0\}\cup \bigcup States(L'),\]
 \[Assignments_{L',States_{L'}}=\bigcup\{Assignments(L', State_{i})\}^{State_{i}\in States_{L'}} \]
@@
 \label{section:FailureTimer}
-
-\TODO{Simon: reduce...}
 
@@
 connectors of the BIP model are encoded as synchronisation vectors,
-\noteSB{Eric, please check whether this is ok.}\hl{with ports
-  representing the actions of the environment used as global actions}.
+with ports
+  representing the actions of the environment used as global actions.
 Each connector that does not involve triggers is trivially encoded by
@@
 3 reachable global states (out of the possible 6) and 12 open
-transitions, is shown in Figure~\ref{schema:resultOA1}.\noteSB{Eric, in the state 20, $b0$ should always be $false$: $\PortFail(true)$ is not possible in Control, and the safety property (\ref{eq:FM:safety}) does not hold otherwise.}
+transitions, is shown in Figure~\ref{schema:resultOA1}.
+%% \noteSB{Eric, in the state 20, $b0$ should always be $false$: $\PortFail(true)$ is not possible in Control, and the safety property (\ref{eq:FM:safety}) does not hold otherwise.}
 
@@
                 297 ms  
-		%% \\\hline\specialrule{0em}{3pt}{3pt}
-		%% SimpleProt    			&
-                %% 7/260 OTs           &
-                %% 7/57 OTs
-                %% \\\specialrule{0em}{1pt}{1pt}
-
-                %% (no holes)&
-                %% 1536 ms 				&
-                %% 359 ms  
-%                \\\specialrule{0em}{1pt}{1pt}
-%                \textsl{for any sort} & & $=,\ \ne$
-		%% \\\hline\specialrule{0em}{1pt}{1pt}
-		%% SimpleProt    			&
-                %% 19/836 OTs           &
-                %% 19/185 OTs
-                %% \\\specialrule{0em}{1pt}{1pt}
-
-                %% (with 2 client holes)&
-                %% 2496 ms 				&
-                %% 844 ms  
 		\\\hline\specialrule{0em}{1pt}{1pt}
@@
   of transitions of each PLTS is finite, rule Tr1 is 
-  applied a finite finite number of times. Therefore, each internal loop of Algorithm~1 terminates, and we obtain finitely many deduction trees and
+  applied a finite number of times. Therefore, each internal loop of Algorithm~1 terminates, and we obtain finitely many deduction trees and
   open transitions.

### 2019-03-30 2017-Xudong-SMT/ActaInformatica.tex
start of proof3

@@
 \ERIC{Proof sketch:}
-
-  \begin{itemize}
-   \item $L1$ = original set of transitions by Algorithm 1, after
-      satisfiability check (i.e. after line 11), using assignments
-      from the whole state space.
-   \item $L2$ = original set of transitions by Algorithm 1, after
-      satisfiability check (i.e. after line 11), using assignments
-      from the original on-the-fly search.
-
-    \item $L1-reach$ = final set of OTs of Algorithm 1, as computed
-        by an iterative application of makeReachableSubAutomaton (line
-        12) up to fixpoint.
-      \item $L2-reach$ = final set of OTs of Algorithm 2, as computed
-          by line 13, as computed
-        by an iterative application of makeReachableSubAutomaton (line
-        16) up to fixpoint.
-  \end{itemize}
 

### 2019-03-31 2017-Xudong-SMT/ActaInformatica.tex
Correct some typos in proof of Th.2
AO seems the wrong typing of OA, as the result is OA in line 12 of Alg.
a little more

@@
 \State $\mathit{OA_0}$=makeReachableSubAutomaton($\mathit{InitState}(P),L1)$;
-\Repeat $\mathit{OA_n}$=RefineReachableSubAutomaton($\mathit{AO_{n-1}}$)
+\Repeat $\mathit{OA_n}$=RefineReachableSubAutomaton($\mathit{OA_{n-1}}$)
 \Until  $\mathit{OA_n}=\mathit{OA_{n-1}}$; \Comment Fixpoint reached
@@
 \State $\mathit{OA_0}$=makeReachableSubAutomaton($\mathit{InitState}(P),L2)$;
-\Repeat $\mathit{OA_n}$=RefineReachableSubAutomaton($\mathit{AO_{n-1}}$)
+\Repeat $\mathit{OA_n}$=RefineReachableSubAutomaton($\mathit{OA_{n-1}}$)
 \Until  $\mathit{OA_n}=\mathit{OA_{n-1}}$;
@@
     \item $L1_{reach}$: the final set of OTs of Algorithm 1, as computed
-      by line 12 (as $AO_0$). Without assignments the following
+      by line 12 (as $OA_0$). Without assignments the following
       refinement step will do nothing, the fixpoint is already reached.
@@
     \item $L2_{reach}$: the final set of OTs of Algorithm 2, as computed
-          by line 13. Here also $AO_n = AO_0$.
+          by line 13. Here also $OA_n = OA_0$.
 \end{itemize}
@@
 We will prove by induction on the distance from the original state,
-that $\forall S \in L0. \forall n \in \mathbb{N}. S \in States(L2_{reach}) \land |S|_{l2_{reach}}=n => S
+that $\forall S \in L0. \forall n \in \mathbb{N}. S \in States(L2_{reach}) \land |S|_{L2_{reach}}=n \Rightarrow S
 \in States(L1_{reach})$, and vice-versa.
@@
   Suppose our property is true for distance $n$, and
-  suppose $|S|_{L2_{reach}}=n+1$, then there exist a chain
+  suppose $|S|_{L2_{reach}}=n+1$, then there exists a chain
   $S_0\xrightarrow{l_1}S_1\xrightarrow{l_2}...S_{n}\xrightarrow{l_{n+1}}S$
@@
   $L2_{reach}\subseteq L2_{sat}$, $l_{n+1} \in L2_{sat}$, meaning 
-  it's predicate is satisfiable.
+  its predicate is satisfiable.
 

### 2019-03-31 2017-Xudong-SMT/ActaInformatica.tex
some typos corrected

@@
 but it also allows 
-for more general mechanisms, like gate negotiation in Lotos~\cite{LotosISO89}, or broadcast
+for more general mechanisms, like gate negotiation in LOTOS~\cite{LotosISO89}, or broadcast
 communications.
@@
 \State $\mathit{OA_0}$=makeReachableSubAutomaton($\mathit{InitState}(P),L1)$;
-\Repeat $\mathit{OA_n}$=RefineReachableSubAutomaton($\mathit{OA_{n-1}}$)
+\Repeat $\mathit{OA_n}$=RefineReachableSubAutomaton($\mathit{AO_{n-1}}$)
 \Until  $\mathit{OA_n}=\mathit{OA_{n-1}}$; \Comment Fixpoint reached
@@
 \State $\mathit{OA_0}$=makeReachableSubAutomaton($\mathit{InitState}(P),L2)$;
-\Repeat $\mathit{OA_n}$=RefineReachableSubAutomaton($\mathit{OA_{n-1}}$)
+\Repeat $\mathit{OA_n}$=RefineReachableSubAutomaton($\mathit{AO_{n-1}}$)
 \Until  $\mathit{OA_n}=\mathit{OA_{n-1}}$;
@@
  managed by the two algorithms both are subsets of the cartesian
- product of the pLTS states, as defined in page \pageref{def-states}. In a
+ product of the PLTS states, as defined in page \pageref{def-states}. In a
  similar way, the set of state variables attached to each state are
@@
  transitions requires a little more care, because within the
- MakeTransitions function, fresh variables are created everytime a
+ $MakeTransitions$ function, fresh variables are created everytime a
  synchronisation vector is used (this occurs within the $MkPred$ and
  $matching$ functions). However, given a global state, the call of
- $MakeTransitions$ will always returns exactly the same set of OTs, up to
+ $MakeTransitions$ will always return exactly the same set of OTs, up to a
 renaming of these fresh variables. When this is not ambiguous, we will
-speak of equality (of transitions, and of open automata) when we
-should say ``up to renaming of fresh variables''.
+speak of equality (of transitions, and of open automata) without the phrase ``up to a renaming of fresh variables''.
 
@@
  \begin{itemize}
-    \item $L0$: the original set of transitions by Algorithm 1
+    \item $L0$: the original set of transitions by Algorithm~\ref{alg1}
       (i.e. before line 11), 
-    \item $L1_{sat}$:  the original set of transitions by Algorithm 1, after
+    \item $L1_{sat}$:  the original set of transitions by Algorithm~\ref{alg1}, after
       satisfiability check (i.e. after line 11),
-    \item $L1_{reach}$: the final set of OTs of Algorithm 1, as computed
+    \item $L1_{reach}$: the final set of OTs of Algorithm~\ref{alg1}, as computed
       by line 12 (as $OA_0$). Without assignments the following
       refinement step will do nothing, the fixpoint is already reached.
-    \item $L2_{sat}$: the original set of transitions by Algorithm 3
+    \item $L2_{sat}$: the original set of transitions by Algorithm~\ref{alg3}
       (i.e. before line 13), 
-    \item $L2_{reach}$: the final set of OTs of Algorithm 2, as computed
+    \item $L2_{reach}$: the final set of OTs of Algorithm~\ref{alg3}, as computed
           by line 13. Here also $OA_n = OA_0$.
+   \item $States: \overline{OT}\rightarrow\overline{State}$:  the function that
+computes the set of target states of a set of OTs.  
+  \item $Rename:  L1_{reach} \rightarrow L2_{reach}$:  a function that keeps state names of transitions but renames fresh variables in the transition labels.
 \end{itemize}
-
-\paragraph{States:} for each of these, define
- $States: \overline{OT}\rightarrow\overline{State}$ the function
-computing the set of target states of a set of OTs. \\
-\noindent
-\emph{Transitions:} between two sets of open transitions computed
-by the algorithms, define $Rename:  L1_{reach} \rightarrow L2_{reach}$
-which is the function renaming fresh variables.
 
@@
 %% filtering step, so $L1_{sat}=L1_{reach}$ and $L2_{sat}=L2_{reach}$.
-We want to prove that $L1_{reach}=L2_{reach}$, that will imply
-the equality of the 2 open automata.
+
+\smallskip
+We now prove that $L1_{reach}=L2_{reach}$, which will imply
+the equality of the two open automata.
 
@@
 The only difference between the main loops of the algorithms is that 
-algorithm~\ref{alg3} only retains the satisfiable OTs (line 6-7), so 
-algorithm~\ref{alg3} computes less transitions than
-algorithm~\ref{alg1}. Formaly $L2_{reach}\subseteq  L2_{sat} \subseteq L0$, and as a consequence $States(L2_{reach})\subseteq  States(L0)$, so we have:\\
+Algorithm~\ref{alg3} only retains the satisfiable OTs (lines 6-7), so 
+Algorithm~\ref{alg3} computes fewer transitions than
+Algorithm~\ref{alg1}. Formally, we have that $L2_{reach}\subseteq  L2_{sat} \subseteq L0$, and as a consequence $States(L2_{reach})\subseteq  States(L0)$, i.e.,\\
 \centerline{$\forall \ostate{\overline{u}}\in States(L2_{reach}), \exists\ostate{\overline{t}}\in States(L0), \ostate{\overline{t}}=\ostate{\overline{u}}$}
@@
 $S_0\xrightarrow{l_1}S_1\xrightarrow{l_2}...S_{n-1}\xrightarrow{l_{n}}S$
-  from the initial state $S_0$, with $\forall k\in [1..n], l_k \in L$.
+  from the initial state $S_0$, with $l_k \in L$ for each $k\in [1..n]$.
 
@@
 We will prove by induction on the distance from the original state,
-that $\forall S \in L0. \forall n \in \mathbb{N}. S \in States(L2_{reach}) \land |S|_{L2_{reach}}=n \Rightarrow S
+that $\forall S \in L0. \forall n \in \mathbb{N}. S \in States(L2_{reach}) \land |S|_{l2_{reach}}=n => S
 \in States(L1_{reach})$, and vice-versa.
@@
   $S_0\xrightarrow{l_1}S_1\xrightarrow{l_2}...S_{n}\xrightarrow{l_{n+1}}S$
-  with all $l_k \in L2_{reach}$. In particular, as
-  $L2_{reach}\subseteq L2_{sat}$, $l_{n+1} \in L2_{sat}$, meaning 
+  with all $l_k \in L2_{reach}$. In particular, since
+  $L2_{reach}\subseteq L2_{sat}$, we have that $l_{n+1} \in L2_{sat}$ and
   its predicate is satisfiable.
@@
   By induction hypothesis, we get $S_{n} \in States(L1_{reach})$, so during the
-  call of $makeReachableSubAutomaton$ in algorithm~\ref{alg1}, line 12, the OT
-  $S_n \xrightarrow{l_{n}}S$ will be check and found SAT, so
+  call of $makeReachableSubAutomaton$ in Algorithm~\ref{alg1}, line 12, the OT
+  $S_n \xrightarrow{l_{n}}S$ will be checked and found SAT, so
   $S \in States(L1_{reach})$.
 
-  Conversely if $|S|_{L1_{reach}}=n+1$, we get a similar chain, in
-  $L1_{reach}$, with $S_n \xrightarrow{l_{n}}S, S_n \in
-  States(L1_{reach})$, and $l_n$ satisfiable. By induction, we have
+  Conversely, if $|S|_{L1_{reach}}=n+1$, we get a similar chain in
+  $L1_{reach}$, with the transition $S_n \xrightarrow{l_{n}}S$.  Then $ S_n \in
+  States(L1_{reach})$ and $l_n$ is satisfiable. By induction, we have
   $S_n \in States(L2_{reach})=States(L2_{sat})$, so $l_n$ will have
-  been checked ``on-the-fly'', in line 6 of algorithm~\ref{alg3},
-  the OT $S_n \xrightarrow{l_{n}}S$ added to $L2_{sat}$, and we
-  conclude $S \in States(L2_{reach})$.
-
-Remember $L0$ is finite, so we conclude $L1_{reach}=L2_{reach}$, and $States(L1_{reach})=States(L2_{reach})$.
+  been checked ``on-the-fly'', in line 6 of Algorithm~\ref{alg3}. Then
+  the transition $S_n \xrightarrow{l_{n}}S$ will be added to $L2_{sat}$, and thus $S \in States(L2_{reach})$.
+
+Note that $L0$ is finite, so we conclude $L1_{reach}=L2_{reach}$, and $States(L1_{reach})=States(L2_{reach})$.
 
@@
   version, meaning the reachability (with assignments) step is
-  iterated up to fixpoint.
+  iterated up to fixed points.
 
@@
   \label{Th:CorrectnessWithAssignments}
-In the general case, if a pNet (verifying the finiteness conditions of theorem 1), contains some assignments to state variables, the smart algorithm computes 
+In the general case, if a pNet (verifying the finiteness conditions of Theorem 1), contains some assignments to state variables, the smart algorithm computes 
 the same open automaton as that of Algorithm 1 up to a renaming of variables in the transition labels.
@@
 \begin{proof}
-  Define the OT sets $L0, L1_{sat}, L2_{sat}, L2_{reach}$ as previously, and:
+  Define the OT sets $L0, L1_{sat}, L2_{sat}, L2_{reach}$ and the function $States$ as in the proof of Theorem~\ref{Th:CorrectnessWithoutAssignments}, and
 
   \begin{itemize}
-    \item $L1_{reach*}$ = final set of OTs of Algorithm 1, as computed
-        by an iterative application of makeReachableSubAutomaton (line
-        14) up to fixpoint.
-      \item $L2_{reach*}$ = final set of OTs of Algorithm 2, as computed
-        by an iterative application of makeReachableSubAutomaton (line
-        16) up to fixpoint.
+    \item $L1_{reach*}$: the final set of OTs of Algorithm~\ref{alg1}, as computed
+        by an iterative application of $makeReachableSubAutomaton$ (line
+        14) up to a  fixed point.
+      \item $L2_{reach*}$: the final set of OTs of Algorithm~\ref{alg3}, as computed
+        by an iterative application of $makeReachableSubAutomaton$ (line
+        16) up to a fixed point.
+        \item $Assignments : \overline{OT}\ \times State\rightarrow \overline{Assign}$: the function of
+        computing the set of assignments of a global state from a given set of OTs.
   \end{itemize}
 
-?? In Theorem 2, we have already proved that the result automata $OA_1$ and $OA_2$ of two algorithms are the same if the pNet contains no assignment to its state variables.
-
-We define the function $States$ as before, and the function $Assignments : \overline{OT}\ \times State\rightarrow \overline{Assign}$
-computing the set of assignments of a global state from a given set of OTs.
-
+%?? In Theorem 2, we have already proved that the result automata $OA_1$ and $OA_2$ of the two algorithms are the same if the pNet contains no assignment to its state variables.
+
+\smallskip
 The structure implicitly computed by both algorithms is a triple $ Aut= \langle \overline{OT}, \overline{State},\\ \overline{Assign}\rangle$.
-
-Then the assignments set of $OA_1$ is $\{Assignments(L1, S_i)\}^{S_i\in States(L1)}$ and $OA_2$ is $\{Assignments(L2_{sat}, S_j)\}^{S_j\in States(L2_{sat})}$. The result triples are:  
+The assignments set of $OA_1$ is $\{Assignments(L1, S_i)\}^{S_i\in States(L1)}$ and that of $OA_2$ is $\{Assignments(L2_{sat}, S_j)\}^{S_j\in States(L2_{sat})}$. The result triples are:  
 \noindent
 \begin{align*}
-Aut_1 = \langle L1_{sat}, States(L1_{sat}), \{Assignments(L1, S_i)\}^{S_i\in States(L1)}\rangle\\
-Aut_2 = \langle L2_{sat}, States(L2_{sat}), \{Assignments(L2_{sat}, S_j)\}^{S_j\in States(L2_{sat})}\rangle \ 
+Aut_1 = \langle L1_{sat}, States(L1_{sat}), \{Assignments(L1, S_i)\}^{S_i\in States(L1)}\rangle\ , \\
+Aut_2 = \langle L2_{sat}, States(L2_{sat}), \{Assignments(L2_{sat}, S_j)\}^{S_j\in States(L2_{sat})}\rangle \  .
 \end{align*}
 
-Based on this triple structure, we define the function $Refine : Aut \rightarrow Aut$ modeling $makeReachableSubAutomaton(S0,OTs)$.
+Based on this triple structure, we define the function $Refine : Aut \rightarrow Aut$ modelling $makeReachableSubAutomaton(S0,OTs)$.
 It uses the assignments of the previous step to refine the computed reachable space:
@@
 \[\bigvee_{Assign_i\in Assignments_{L, States_{L}}}(Pred_{l}\wedge Assign_{i})\text{ is true}.\]
-More transitions could be unsatisfiable after the reduction of the assignments set, so the function need iterate several times.
-Given that in each iteration, the number of triples decreases, so $Refine$ is a monotone function.
-And there exists a sequence \[Aut^n = Refine(Aut^{n-1})\quad s.t.
+More transitions could be unsatisfiable after the reduction of the assignments set, so the function needs to be iterated several times.
+In each iteration, the number of triples decreases, thus there exists a sequence \[Aut^n = Refine(Aut^{n-1})\quad s.t.
 |Aut^n| < |Aut^{n-1}|.\]
-The function terminates if $Aut''$ contains no more unsatisfiable transition, then there is a fixed-point $Aut'' = Refine(Aut'')$ and $|Aut''| = |Refine(Aut'')|$.
-
-Let $Aut''_1$ and $Aut''_2$ be two fixed-points that $Refine(Aut''_1) = Aut''_1$, $Refine(Aut''_2) = Aut''_2$.
+The iteration terminates if $Aut''$ contains no more unsatisfiable transition, then there is a fixed point $Aut'' = Refine(Aut'')$ and $|Aut''| = |Refine(Aut'')|$.
+
+Let $Aut''_1$ and $Aut''_2$ be two fixed points with $Refine(Aut''_1) = Aut''_1$ and $Refine(Aut''_2) = Aut''_2$.
 Focusing on the transition sets in $Aut''_1$ and $Aut''_2$, $L1''_{sat}=L1_{reach}$ and $L2''_{sat}=L2_{reach}$, we need to check their equivalence.
@@
 \[\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L1'_{unsat} \longrightarrow \ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L2'_{unsat}.\]
-Or it is the transition has not removed in the last iteration because of 
+Or it is the transition not removed in the last iteration because of the inclusion
 \[Assignments_{L2_{sat}, States_{L2_{sat}}}\subseteq Assignments_{L1, States_{L1}}.\] 
@@
 
-We check the satisfiability of each open transitions
+We check the satisfiability of each open transition
 using the SMT solver Z3.
@@
 particular because of structured names for the fresh variables generated
-by the algorithm, allowing for tracability of the result~\cite{Avocs-RR}.
+by the algorithms, allowing for tracability of the result~\cite{Avocs-RR}.
 
@@
 in the SMTlib syntax. It contains the declaration
-of the relevent part of the Lotos action algebra sorts 
+of the relevent part of the LOTOS action algebra sorts 
 and constructors, then the declaration of variables, and finally the
@@
 For other data structures  in such models, like records, or
-recursive structures, the user will have to develop its own theories.
+recursive structures, the user will have to develop her own theories.
 Decidability of these theories will condition on the completeness of the
@@
 names from our example.
-In addition, we will include axiomatisation of any required functions
+In addition, we will include the axiomatisation of any required functions
 and predicates of the presentation data-types.
@@
 \begin{itemize}
-	\item to collect all variables in the transition, and declare them (using \texttt{declare-const})
+	\item to collect all variables in the transition, and declare them (using \texttt{declare-const}),
 	\item to check the well-formedness and correct typing of expressions,
@@
 can be composed together.
-Finaly we give some figures illustrating the benefits from the smart
+Finally we give some figures illustrating the benefits of the smart
 algorithm on these examples.
@@
 
-For this example, the tool (using Algorithm 1) builds 408 open transitions, whereof 396
+For this example, the tool (using Algorithm~\ref{alg1}) builds 408 open transitions, whereof 396
 are detected unsatisfiable by Z3.  The resulting open automaton, with
@@
 We have used a running example based on two possible
-encodings of the Enable operator of Lotos. The automata computed with
+encodings of the Enable operator of LOTOS. The automata computed with
 the algorithm can be used to prove equational properties of the

### 2019-03-31 2017-Xudong-SMT/ActaInformatica.tex
cosmetic changes

@@
 
-Implementing these semantics raised several challenges, in order:
+Implementing these semantics raised several challenges:
 \begin{itemize}
@@
 	\item to separate clearly the 
-	algorithm generating the transitions of the open automaton from
+	algorithm generating the transitions of an open automaton from
 	combination of all possible (symbolic) behaviours, and from
@@
 
-\paragraph{Contribution}
+\paragraph{Contribution.}
 In the current work we contribute in the following aspects.
@@
 	\item We implement the interaction between our algorithm and the Z3
-	SMT solver, for checking satisfiability of the transitions
+	SMT solver, for checking the satisfiability of the transitions
 	generated by the algorithm.
@@
 In Section~\ref{section:use-cases} we give a few use-cases, in particular, a BIP
-architecture from the nano-satellite case-study. 
+architecture from the nanosatellite case-study. 
 Finally we conclude and discuss perspectives in Section
@@
 \mathcal{E}_\P\cap\mathcal{A}_\P=\emptyset$;
-naturally action terms will use data expressions as sub-terms.
+ action terms will use data expressions as sub-terms.
 The function $\vars(t)$ identifies the set of variables in a term
@@
 	Given a term algebra $\Talg$, a PLTS is a tuple
-	$PLTS\triangleq\mylangle S,s_0, \to\myrangle$ where:
+	$\langle S,s_0, \to\rangle$, where
 	\begin{itemize}
@@
 %% A pNet is a hierarchical structure, whereof the leaves are PLTSs and holes:
-%% $\pNet::= PLTS~|~\mylangle \pNet_i^{i\in I}, S_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle$,
+%% $\pNet::= PLTS~|~\langle \pNet_i^{i\in I}, S_j^{j\in J}, \symb{SV}_k^{k\in K}\rangle$,
 %% where
@@
 	%% sort~\cite{HMZ-FORTE2016}}
-	$\pNet\triangleq PLTS~|~\mylangle \pNet_i^{i\in I}, J, \symb{SV}_k^{k\in 
-		K}\myrangle$, with $I, J, K$ potentialy infinite,
+	$\pNet\triangleq PLTS~|~\langle \pNet_i^{i\in I}, J, \symb{SV}_k^{k\in 
+		K}\rangle$, with $I, J, K$ potentialy infinite,
 	where
 	\begin{itemize}
-		\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets;
+		\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets.
 		%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which 
@@
 		\item[$\bullet$] $J$ is a set of indexes, called \emph{holes}.
-		$I$ and $J$ are \emph{disjoint}: $I\!\cap\! J=\emptyset$,  $I\!\cup\! J\neq\emptyset$
+		$I$ and $J$ are \emph{disjoint}: $I\!\cap\! J=\emptyset$,  $I\!\cup\! J\neq\emptyset$.
 		%\item[$\bullet$] $\Sort_j \subseteq \AlgAS$ is a set of action terms, denoting the 
@@
 		\item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
-		synchronisation vectors ($K\in\I_\P$). $\forall k\!\in\! K,
+		synchronisation vectors ($K\in\I_\P$).  It is required that \linebreak $\forall k\!\in\! K,
 		\symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k\,|\,g_k$, where
@@
 			J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
-		$\alpha'_k$. The Boolean expression $g_k $, such that $\vars(g_k)\subseteq \bigcup_{l\in 
+		$\alpha'_k$. The Boolean expression $g_k $, with $\vars(g_k)\subseteq \bigcup_{l\in 
 			I_k\uplus J_k}{\vars({\alpha_l})}$, is a guard associated to the vector.
@@
   \includegraphics[width=\linewidth]{ActaXFIG/P-QR}
-  \caption{Composed pNet for ``P>>(Q>>R)''}  \label{schema:enable-composed}
+  \caption{Composed pNet for ``$P>>(Q>>R)$''}  \label{schema:enable-composed}
 \end{minipage}
@@
 
-	To give simple intuitions of the open pNet model and its semantics, we use
+	To give an intuition of the open pNet model and its semantics, we use
 	here a simple example based on the ``Enable'' operator of the LOTOS language.
-	In the Enable expression ``P>>Q'', an \texttt{exit} statement within P
+	In the Enable expression ``$P>>Q$'', an \texttt{exit} statement within $P$
 	terminates the current process, carrying a value $x$ that
-	is captured by the \texttt{accept} statement of Q. 	
+	is captured by the \texttt{accept} statement of $Q$. 	
 	We use a simple action algebra,
@@
 	case, in which we want the vector to apply to any action of $P$
-	except $\delta(z)$.
+	except for $\delta(z)$.
 
 	In Figure \ref{schema:enable-composed}, we enrich our example by
-	composing two occurences of the EnableState pNet. In Section
+	composing two occurences of the $EnableState$ pNet. In Section
         \ref{section:use-case:Enable} we will show how these encodings can
@@
 	\label{def:open-automaton}
-	An \emph{open automaton} is a structure\\ $A =
-	\langle J,\mathcal{S},s_0,\mathcal{T}\rangle$ where:
+	An \emph{open automaton} is a tuple $
+	\langle I, J,\mathcal{S},s_0,\mathcal{T}\rangle$, where
 	\begin{itemize}
@@
 in structured states as $\triangleleft\ldots\triangleright$).
-For any pNet $p$, let $\overline{\mathit{Leaves}} = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be the set of PLTSs at its leaves,
+For any pNet $p$, let $\overline{\mathit{Leaves}} = \langle S_i,{s_i}_0, \to_i\rangle^{i \in L}$ be the set of PLTSs at its leaves,
 then $\mathit{States}(p) = \{\ostate{s_i^{i\in L}}
@@
 A PLTS could be its own single leave:
-$\mathit{States}(\mylangle S,s_0, \to\myrangle) = \{\ostate{s}|\, s \in S\}$.
+$\mathit{States}(\langle S,s_0, \to\rangle) = \{\ostate{s}|\, s \in S\}$.
 The initial state is defined as:
@@
 Let
-$\mylangle\overline{\pNet},J,\symb{SV}_k^{k\in K} \myrangle$
+$\langle\overline{\pNet},J,\symb{SV}_k^{k\in K} \rangle$
 be a pNet. Consider a synchronisation vector $SV_k$, for $k\in K$. We build a
@@
 If we use the data-oriented pNet $EnableData$ from Figure
-\ref{schema:enable-pnets} to build a similar $EnableDataCompLeft$
-``P>>(Q>>R)'' expression, the corresponding open transition would be:
+\ref{schema:enable-pnets} to build a similar $EnableDataCompLeft$  expression
+``$P>>(Q>>R)$'', the corresponding open transition would be:
 
@@
         where $v_1$ and $v_2$ are respectively the state variables of
-        the first and second EnableData pNets. Indeed the global
+        the first and second $EnableData$ pNets. Indeed the global
         state space of this version is reduced to $\ostate{0,0}$, and
@@
   \label{Th:finiteness}
-   Let $pnet=\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ be an open pNet  with leaves $l_i^{i\in I}$ and holes $h_j^{j\in
+   Let $pnet=\langle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\rangle$ be an open pNet  with leaves $l_i^{i\in I}$ and holes $h_j^{j\in
  	J}$, where the sets $I$ and $J$ are finite. Suppose the synchronisation vectors of all pNets 
@@
           \State Add $\mathit{OT}$ to $L$;
-          \State Let $S'$ be the target state of $\mathit{OT}$
-          Add $S'$ to the unexplored states if necessary:
+          \State Let $S'$ be the target state of $\mathit{OT}$;
+          add $S'$ to the unexplored states if necessary:
 	  \IfThen{($S' \not\in U \cup E$)}{Add $S'$ into $U$;}
@@
 
-Algorithm~\ref{alg1} starts with an open pNet, and builds its set of open
+Algorithm~\ref{alg1} starts with an open pNet and builds its set of open
 transitions. Its main loop is a classical residual algorithm: starting
@@
 do not have valid ground instanciations. This is not logically
-incorrect, but is naturaly not an optimal representation. So we prune
+incorrect, but is naturally not an optimal representation. So we prune
 these UNSAT transitions: at the end of the open automaton generation,
@@
 Then we compute the set of reachable transitions and states to build
-the final open automaton (more details in section~\ref{section:BuildingTheOpenAutomaton}).
+the final open automaton (more details in Section~\ref{section:BuildingTheOpenAutomaton}).
 
@@
     cannot be matched (by unification) with the corresponding action expressions
-      on the tuple $C$ (this is strictly stronger than the
+      in the tuple $C$ (this is strictly stronger than the
       previous filter). 
@@
 The only assignments for state variables that happen at the PLTS level
-are as follows: every time the MakeTransitions 
-algorithm is applied on a PLTS, it collects the expressions from the
+are as follows: every time the $MakeTransitions$ method 
+ is applied on a PLTS, it collects the expressions from the
 $Post$ in each transition. 
@@
 
-It shows the case where processes $P$ and $R$ ``try'' to communicate directly, $P$, but this is made impossible by the combination of chosen synchronisation vectors and their guards. This
+It shows the case where processes $P$ and $R$ ``try'' to communicate directly, but this is made impossible by the combination of chosen synchronisation vectors and their guards. This
   mismatch is materialised by the predicate
@@
 checking satisfiability of transitions leaving a given state may
-result in more Unsat transitions. The set of possible
+result in more UNSAT transitions. The set of possible
 assignments computed by the algorithm is an over approximation of
@@
 assignments of the corresponding target states. In
-algorithm~\ref{alg1}, we iterate this procedure, each iteration
+Algorithm~\ref{alg1}, we iterate this procedure, each iteration
 reducing the set of 
@@
 In practice, this could be
-expensive, and it is not incorrect to leave some Unsat OTs in the
+expensive, and it is not incorrect to leave some UNSAT OTs in the
 result. From a  practical point of view, very little will be gained to compute the
@@
 The basic algorithm from the previous section potentially explores some
-areas of the global state-space that will not be reachable after
+areas of the global state space that will not be reachable after
 checking the OTs' predicates for satisfiability. Incorporating the
@@
 state space. We first need to compute a first over-approximation of
-the reachable state space, and assignment sets; this corresponds to
+the reachable state space and assignment sets; this corresponds to
 the automaton $OA_0$ in Algorithm~\ref{alg3}, line 15.
@@
 variables. This does not mean ``data-independency'': we can still have
-guards in the pLTS transitions and in the synchronisation vectors,
-making the behaviour depending on the value of input variables. But
+guards in the PLTS transitions and in the synchronisation vectors,
+making the behaviour depending on the values of input variables. But
 the open automaton needs not to collect the set of possible values dealing
@@
 Figure~\ref{schema:enable-composed}. Its open automaton is shown in
-Figure~\ref{schema:enable3bis}. Building the symmetric system \noteSB{Should this be typeset in math mode?}``(P>>Q)>>R'' in a similar
+Figure~\ref{schema:enable3bis}. Building the symmetric system ``$(P>>Q)>>R$'' in a similar
 way will allow us to prove that they are bisimilar (the Enable
@@
   \end{minipage}
-  \caption{Open Automaton for the term ``P>>(Q>>R)''}
+  \caption{Open Automaton for the term ``$P>>(Q>>R)$''}
   \label{schema:enable3bis}
@@
   \label{def:operationalSemantics}
-  The semantics of a pNet $p$ is an open automaton $A = <Leaves(p),J,\mathcal{S}, s_0,
-  \mathcal{T}>$ where:
+  The semantics of a pNet $p$ is an open automaton $A = \langle Leaves(p),J,\mathcal{S}, s_0,
+  \mathcal{T}\rangle $ where:
   \begin{itemize}
@@
     }
-    { p = \mylangle  S,s_0, \to \myrangle
+    { p = \langle  S,s_0, \to \rangle
       \models
@@
     }
-    {p = \mylangle \pNet_i^{i\in I}, S_j^{j\in J}, \symb{SV}_k^{k\in K}\myrangle
+    {p = \langle \pNet_i^{i\in I}, S_j^{j\in J}, \symb{SV}_k^{k\in K}\rangle
       \models
@@
 %\noindent\textbf{Theorem 1} 
-	Let $pnet=\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ be an open pNet  with leaves $l_i^{i\in I}$ and holes $h_j^{j\in
+	Let $pnet=\langle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\rangle$ be an open pNet  with leaves $l_i^{i\in I}$ and holes $h_j^{j\in
 		J}$, where the sets $I$ and $J$ are finite. Suppose the synchronisation vectors of all pNets 
@@
 \begin{theorem}[Finiteness of open-automata.]\\
-Given an open pNet $pnet=\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ with leaves $l_i^{i\in L}$ and holes $h_j^{j\in
+Given an open pNet $pnet=\langle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\rangle$ with leaves $l_i^{i\in L}$ and holes $h_j^{j\in
   J}$, if the sets $L$ and $J$ are finite, if the synchronization vectors of all pNets 
@@
 
-Given an open pNet $\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in
-    K}\myrangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
+Given an open pNet $\langle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in
+    K}\rangle$ with leaves $pLTS_i^{i\in L}$ and holes $Hole_j^{j\in
   J}$,
@@
 Predicates already have a format declaring what it verifies. According to that previous work, we define the predicates.
-Let $\mylangle\overline{\pNet},\overline{S},\symb{SV}_k^{k\in K} \myrangle$
+Let $\langle\overline{\pNet},\overline{S},\symb{SV}_k^{k\in K} \rangle$
 be a pNet. Choose a synchronisation vector $SV=clone(SV_k) ={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v' \, ,G_k $, for $k\in K$. The

### 2019-03-31 2017-Xudong-SMT/ActaInformatica.tex
more precise decription for the last part of the proof of Th.3

@@
 We have $L'\subseteq L$, and potentially, their target states and corresponding assignments may be reduced:
-\[States(L')=\{S_0\}\cup \bigcup States(L'),\]
+\[States_{L'}=\{S_0\}\cup \bigcup States(L'),\]
 \[Assignments_{L',States_{L'}}=\bigcup\{Assignments(L', State_{i})\}^{State_{i}\in States_{L'}} \]
@@
 
-In one single iteration, satisfiability of a transition $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L$ is checked through whether 
+In one single iteration, the satisfiability of a transition $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L$ is checked through whether 
 \[\bigvee_{Assign_i\in Assignments_{L, States_{L}}}(Pred_{l}\wedge Assign_{i})\text{ is true}.\]
-More transitions could be unsatisfiable after the reduction of the assignments set, so the function needs to be iterated several times.
+More transitions could become unsatisfiable after the reduction of the assignments set, so the function needs to be iterated several times.
 In each iteration, the number of triples decreases, thus there exists a sequence \[Aut^n = Refine(Aut^{n-1})\quad s.t.
@@
 &\bigvee_{Assign_i\in Assignments_{L1, States_{L1}}} (Pred_{l}\wedge Assign_i)\text{ is false}\\
-\longrightarrow&\bigvee_{Assign_j\in Assignments_{L2_{sat}, States_{L2_{sat}}}} (Pred_{l}\wedge Assign_j)\text{ is false}.
+\text{implies }&\bigvee_{Assign_j\in Assignments_{L2_{sat}, States_{L2_{sat}}}} (Pred_{l}\wedge Assign_j)\text{ is false}.
 \end{align*}
-The relation that $\forall\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}} \in L1_{unsat},\exists\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}} \in L2_{unsat}$, implies that $L1_{unsat}\subseteq L2_{unsat}.$
+From the relation $\forall\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}} \in L1_{unsat},\exists\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}} \in L2_{unsat}$, it can be implied that $L1_{unsat}\subseteq L2_{unsat}.$
 
@@
 Let $L1'_{sat}=L1_{sat}-L1_{unsat}$ and $L2'_{sat}=L2_{sat}-L2_{unsat}$
-Then in the next iteration, the unsatisfiable transition $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}$ removed from $L1'_{sat}$ might be the same transition (up to renaming) removed from $L2'_{sat}$.
-In this case,
-\[\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L1'_{unsat} \longrightarrow \ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L2'_{unsat}.\]
+Then in the next iteration, the unsatisfiable transition $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L1'_{unsat}$ removed from $L1'_{sat}$ has two cases, we use $L1'_{unsat1}$ and $L1'_{unsat2}$ where $L1'_{unsat1}+L1'_{unsat2}=L1'_{unsat}$ to present them.
+In the first case, it might be the same transition (up to renaming) removed from $L2'_{sat}$,
+\[\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L1'_{unsat1}\longrightarrow\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L2'_{unsat}.\]
+
 Or it is the transition not removed in the last iteration because of the inclusion
@@
 so those transitions will be removed this time. In this case,
-\[\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L1'_{unsat} \longrightarrow \ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\notin L2_{sat}.\]
-
-By induction, if there is no more unsatisfiable transitions in $L2''_{sat}$, $L1''_{sat}$ continues removing all the transitions not in $L2''_{sat}$, until $L1_{reach}=L2_{reach}$.
+\[\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L1'_{unsat2}\longrightarrow\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\notin L2_{sat}.\]
+
+By induction, if there is no more unsatisfiable transitions in $L2''_{sat}$, so $L2''_{unsat}$ is an empty set and then $L1'_{unsat1}$ is also empty as $L1'_{unsat1}\subseteq L2''_{unsat}$.
+The transitions to remove should only belong to $L1'_{unsat2}\nsubseteq L2''_{sat}$.
+So the iteration continues removing all the transitions not in $L2''_{sat}$, until $L1_{reach}=L2_{reach}$.
 It implies that $States_{L1_{reach}}=States_{L2_{reach}}$ and

### 2019-03-31 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf. paper: Revised sections 5.2 and 5.3 (Failure Monitor architecture). Significant changes of the characteristic properties of the architecture.

--- 2019-03-31 2017-Xudong-SMT/ActaInformatica.tex
@@
 %% \usepackage[list=true]{subcaption}
+
+\usepackage{tikz}
+\usetikzlibrary{matrix,arrows,decorations.pathmorphing,shapes}
+\usetikzlibrary{decorations.markings}
+\usetikzlibrary{calc,positioning}
+
+%% \tikzset{
+%%   negated/.style={
+%%     decoration={
+%%       markings,
+%%       mark=at position 0.5 with {\node[transform shape] (tempnode) {$/$};},
+%%     },
+%%     postaction={decorate},
+%%   },
+%% }
+
+%% \tikzset{label/.style={text=blue,font=\normalsize}}
+%% \tikzset{box/.style={fill=yellow,draw=brown}}
+%% \tikzset{port north/.style={fill=white,draw=brown,anchor=north,minimum size=1.2em}}
+%% \tikzset{port east/.style={fill=white,draw=brown,anchor=east}}
+%% \tikzset{port west/.style={fill=white,draw=brown,anchor=west}}
+%% \tikzset{port south/.style={fill=white,draw=brown,anchor=south}}
+
+\newenvironment{tikzlts}[1][15mm]{\begin{tikzpicture}
+[->,>=stealth',shorten >=1pt,auto,node distance={#1},thick,draw=black,
+state/.style={ellipse,draw=black,font=\sffamily},align=center,text=black]} %,fill=blue!20 \large\bfseries
+{\end{tikzpicture}}
 
@@
 \newcommand{\EU}[3][\ ]{\ensuremath{\mathtt{E}\left[#2\ \mathtt{U}\ #3\right]#1}}
+\newcommand{\AU}[3][\ ]{\ensuremath{\mathtt{A}\left[#2\ \mathtt{U}\ #3\right]#1}}
 
@@
 
+Notice that the model in Figure~\ref{schema:ArchFailure:BIP} allows
+$\PortReset$ to happen in any state.  However, it is implied that,
+when the coordinator $\NameCtrl$ is in state $\cstate{2}$, this
+$\PortReset$ is ``asked for'' by the architecture (it follows the
+firing of $\PortAsk$), whereas in other states the corresponding
+transition reflects an ``external'' reset.  Although this can be
+formalised in the model using data variables, we have chosen not to do
+so for the sake of simplicity.
+
 Intuitively, application of the Failure Monitor architecture ensures
@@
 %
-1)~the safety property \emph{``There is always a possibility to reset
-  the system after a single failure''} (\ie without additional
-failures having to occur in the meantime) specified using CTL as
+1)~the safety property \emph{``A reset is never asked for unless a failure occurs''} specified using CTL as
 %
@@
   \label{eq:FM:safety}
-  \AG
-  \bigl(\PortFail \rightarrow
-  \EX \EU[]{\lnot \PortFail}{\PortReset}\bigr)
+  %% \AG
+  %% \bigl(\PortFail \rightarrow
+  %% \EX \EU[]{\lnot \PortFail}{\PortReset}\bigr)
+  \AW[]{\lnot \PortAsk}{\PortFail}
 \end{equation}
 %
-and 2)~the liveness property \emph{``a reset will be fired when asked
-  for by a timeout''}:
+and 2)~the liveness property \emph{``in the absence of an external
+  reset, a reset can always be asked for after a non-transient
+  failure''}:
 %
@@
   \label{eq:FM:liveness}
-  \mathtt{AG}(\PortAsk \rightarrow \mathtt{AF}\ \PortReset).
+  %% \mathtt{AG}(\PortAsk \rightarrow \mathtt{AF}\ \PortReset).
+  \AG \bigl(
+  \PortFail \rightarrow \EU[]{(\lnot \PortReset \land \lnot \PortResume)}{\PortAsk}
+  \bigr)
 \end{equation}
@@
   \centering
-  \includegraphics[width=0.9\columnwidth]{ActaXFIG/Double-OA}
+  %% \includegraphics[width=0.9\columnwidth]{ActaXFIG/Double-OA}
+  \resizebox{\columnwidth}{!}{
+  \begin{tikzlts}
+    \node[state] (0000) {0000};
+    \node[state, above right= 10mm and 30mm of 0000] (1010) {1010};
+    \node[state, below right= 10mm and 30mm of 0000] (0101) {0101};
+    \node[state, below right= 10mm and 30mm of 1010] (1111) {1111};
+    \node[state, above right= 15mm and 20mm of 1010] (2200) {2200};
+
+    \path[draw,->]
+    (0000.135)
+    .. controls +(-7mm,3mm) and +(-3mm,7mm) ..
+    node {reset}
+    (0000.120)
+    ;
+
+    \path
+    (0000)
+    edge[loop left] node[left] {resume1(*)} (0000)
+    edge[bend left] node[above] {fail1(true)} (1010)
+    edge[bend right] node[below] {fail2(true)} (0101)
+    ;
+
+    \path[draw,->]
+    (0000.-120)
+    .. controls +(-3mm,-7mm) and +(-7mm,-3mm) ..
+    node[below left] {resume2(*)}
+    (0000.-135)
+    ;
+
+    \path[draw,->]
+    (1111.60)
+    .. controls +(3mm,7mm) and +(7mm,3mm) ..
+    node[above right] {fail1(*)}
+    (1111.45)
+    ;
+
+    \path
+    (1111)
+    edge node {reset} (0000)
+    edge[loop right] node[right] {fail2(*)} (1111)
+    edge[out=170,in=-20] node[left] {resume2(true)} (1010)
+    edge[out=-170,in=20] node[left] {resume1(true)} (0101)
+    ;
+
+    \path[draw,->]
+    (1111.-45)
+    .. controls +(7mm,-3mm) and +(3mm,-7mm) ..
+    node[below right] {\begin{tabular}{@{}l@{}}
+        tick\\
+        {}[t1<Max1 \& t2<Max2]\\
+        \{t1:=t1+1; t2:=t2+1\}
+    \end{tabular}}
+    (1111.-60)
+    ;
+
+    \path[draw,->]
+    (1111) edge
+    node[above right] {\begin{tabular}{@{}l@{}}
+        ask\\
+        {}[t1>=Max1 \& t2>=Max2]
+    \end{tabular}}
+    (2200)
+    ;
+
+    \path
+    (1010)
+    edge[out=-170,in=30] node[above] {reset} (0000)
+    edge[out=-150,in=20] node[below] {resume1(true)} (0000)
+    edge[bend left] node[above] {fail2(true)} (1111)
+    ;
+
+    \path[draw,->]
+    (1010.45)
+    .. controls +(7mm,3mm) and +(3mm,7mm) ..
+    node[above right] {fail1(*)}
+    (1010.80)
+    ;
+
+    \path[draw,->]
+    (1010.100)
+    .. controls +(-3mm,7mm) and +(-7mm,3mm) ..
+    node[above left] {resume2(*)}
+    (1010.135)
+    ;
+
+    \path
+    (0101)
+    edge[out=170,in=-30] node[below] {reset} (0000)
+    edge[out=150,in=-20] node[above] {resume2(true)} (0000)
+    edge[bend right] node[below right] {fail1(true)} (1111)
+    ;
+
+    \path[draw,->]
+    (0101.-45)
+    .. controls +(7mm,-3mm) and +(3mm,-7mm) ..
+    node[below right] {fail2(*)}
+    (0101.-80)
+    ;
+
+    \path[draw,->]
+    (0101.-100)
+    .. controls +(-3mm,-7mm) and +(-7mm,-3mm) ..
+    node[below left] {resume1(*)}
+    (0101.-135)
+    ;
+
+    \path[draw,->]
+    (2200.west)
+    .. controls +(left:5cm) ..
+    node[above left] {reset}
+    (0000.80)
+    ;
+
+    \path[draw,->]
+    (2200.0)
+    .. controls +(7mm,0) and +(3mm,-7mm) ..
+    node[right] {fail2(*)}
+    (2200.-20)
+    ;
+
+    \path[draw,->]
+    (2200.40)
+    .. controls +(3mm,7mm) and +(7mm,3mm) ..
+    node[above right] {fail1(*)}
+    (2200.20)
+    ;
+
+    \path[draw,->]
+    (2200.100)
+    .. controls +(-3mm,7mm) and +(3mm,7mm) ..
+    node[above] {resume2(*)}
+    (2200.80)
+    ;
+
+    \path[draw,->]
+    (2200.160)
+    .. controls +(-7mm,3mm) and +(-3mm,7mm) ..
+    node[left] {resume1(*)}
+    (2200.150)
+    ;
+  \end{tikzlts}}
   \caption{The resulting automaton}
@@
 automaton computed for the combined architecture of
-Figure~\ref{schema:ArchFailure:BIP:Double}.  It indicates that the two
-timers are forced to be synchronous: each can only tick after the
-other has also started, and then they will tick, reset, and timeout,
-synchronously.
+Figure~\ref{schema:ArchFailure:BIP:Double}.
 %
-\hl{This is a very strong assumption, and we are working on a more
-flexible specification (at BIP level) to release this hypothesis while
-keeping the safety properties of the composition.}
-
-\noteInSB{The idea was that, by analysing the combination, we observe
-  that the architecture does not compose well with itself, generating
-  a deadlock (or an implicit deadlock, where only $false$ transitions
-  canb be fired.  Based on this observation, we were to improve it
-  accodingly.  The problem is that I do not see any deadlocks in
-  Figure~\ref{schema:ArchFailure:Double:OA}.  I presume that some of
-  the asterisks should be only $false$ or something of a kind.}
+Comparing the guards of the transitions $\PortTick$ and $\PortAsk$
+leaving state $1111$, we see that $\PortAsk$ can never be taken,
+unless $\mathrm{Max1} = \mathrm{Max2}$.  This illustrates the
+\emph{interference} phenomenon discussed in
+\cite{AttieBBJS16-architectures-faoc}, showing that the liveness
+property (\ref{eq:FM:liveness}) is not preserved when two copies of
+the Failure Monitor architecture are composed together.\footnote{%
+%
+  One of the main results of \cite{AttieBBJS16-architectures-faoc}
+  states that in a system obtained by an application of several
+  architectures, liveness properties are preserved if these
+  architectures are \emph{pair-wise non-interfering}.  However, no
+  results were provided to check whether two are architectures are
+  interfering or not.
+%
+} In this example, the interference is caused by the strong
+synchronisation of the $\PortTick$ ports of the two architectures.  It
+can be avoided by replacing the \mbox{$\PortTick
+  \bullet\!\!\!-\!\!\!-\!\!\!\bullet \NameTimer.\PortTick$} connector
+in Figure~\ref{schema:ArchFailure:BIP} by \mbox{$\PortTick
+  \blacktriangleright\!\!\!-\!\!\!-\!\!\!\bullet
+  \NameTimer.\PortTick$} and applying the so-called \emph{maximal
+  progress} whereby, whenever possible, the interaction $\{\PortTick,
+\NameTimer.\PortTick\}$ is preferred to the firing of $\PortTick$
+alone.  However, this fix goes beyond the scope of the current paper.
+
+%% It indicates that the two
+%% timers are forced to be synchronous: each can only tick after the
+%% other has also started, and then they will tick, reset, and timeout,
+%% synchronously.
+%% %
+%% \hl{This is a very strong assumption, and we are working on a more
+%% flexible specification (at BIP level) to release this hypothesis while
+%% keeping the safety properties of the composition.}
+
+%% \noteInSB{The idea was that, by analysing the combination, we observe
+%%   that the architecture does not compose well with itself, generating
+%%   a deadlock (or an implicit deadlock, where only $false$ transitions
+%%   canb be fired.  Based on this observation, we were to improve it
+%%   accodingly.  The problem is that I do not see any deadlocks in
+%%   Figure~\ref{schema:ArchFailure:Double:OA}.  I presume that some of
+%%   the asterisks should be only $false$ or something of a kind.}
 

### 2019-03-31 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf. paper (minor): corrected a misprint and changed >= to \geq

@@
         tick\\
-        {}[t1<Max1 \& t2<Max2]\\
+        {}[t1 < Max1 \& t2 < Max2]\\
         \{t1:=t1+1; t2:=t2+1\}
@@
         ask\\
-        {}[t1>=Max1 \& t2>=Max2]
+        {}[t1 $\geq$ Max1 \& t2 $\geq$ Max2]
     \end{tabular}}
@@
   architectures are \emph{pair-wise non-interfering}.  However, no
-  results were provided to check whether two are architectures are
+  results were provided to check whether two architectures are
   interfering or not.

### 2019-04-01 2017-Xudong-SMT/ActaInformatica.tex
more cosmetic changes

@@
 We also propose and implement an optimised
-	algorithm that performs part of the pruning on-the-fly, and show 
+	algorithm that performs part of the pruning on the fly, and show 
 	its correctness with respect to the original one.
@@
 	%  \noteSB{I think this can be removed}\hl{All sorts and operator names must be distinct.}
-	Constructors of arity 0 are called \emph{constants}, and denoted $\mathit{Consts}(\APres)$.
+	Constructors of arity 0 are called \emph{constants}, and denoted by $\mathit{Consts}(\APres)$.
 	%  $\mathit{Consts}(\APres) = \{\mathit{Con} \in \mathit{Constrs}\,|\, \mathit{arity}(\mathit{Con})=0\}$.
@@
 A state of an open pNet is a tuple of the
-states of its leaves (in which we denote tuples
-in structured states as $\triangleleft\ldots\triangleright$).
-For any pNet $p$, let $\overline{\mathit{Leaves}} = \langle S_i,{s_i}_0, \to_i\rangle^{i \in L}$ be the set of PLTSs at its leaves,
+states of its leaves. We denote tuples
+in structured states in the form $\triangleleft\ldots\triangleright$.
+For any pNet $p$, let $\langle S_i,{s_i}_0, \to_i\rangle^{i \in L}$ be the set of PLTSs at its leaves,
 then $\mathit{States}(p) = \{\ostate{s_i^{i\in L}}
@@
 \end{theorem}
-  Remark that all the elements of such pNets and open automata are symbolic, and they can represent many classes of unbounded systems.
+Notice that all the elements of such pNets and open automata are symbolic, and they can represent many classes of unbounded systems.
 
@@
 \label{section:implementation}
-In this section we describe the algorithm implementing the pNet
+In this section we describe an algorithm implementing the pNet
 semantics, its new ``on-the-fly'' version, and the interaction with the
@@
 \Repeat $\mathit{OA_n}$=RefineReachableSubAutomaton($\mathit{OA_{n-1}}$)
-\Until  $\mathit{OA_n}=\mathit{OA_{n-1}}$; \Comment Fixpoint reached
+\Until  $\mathit{OA_n}=\mathit{OA_{n-1}}$;   \hfill $\setminus \setminus$ Fixed point reached
 \State \Return $\mathit{OA_n}$;
@@
 Before the SAT checking step, it may contain symbolic transitions that
-do not have valid ground instanciations. This is not logically
+do not have valid ground instantiations. This is not logically
 incorrect, but is naturally not an optimal representation. So we prune
@@
 When applying a rule to a PLTS at the leaves, we simply take the PLTS transitions of the
-corresponding local state and use the semantic rule to build the OT.
-When applying a rule to a pNet node we use two methods, combining and
-matching, to generate the open transitions in a hierarchical manner,
+corresponding local state and use the semantic rules to build the OT.
+When applying a rule to a pNet node we use two methods, \emph{combining} and
+\emph{matching}, to generate the open transitions in a hierarchical manner,
 as shown in Algorithm~\ref{alg2}. This method directly manages the
@@
   \item if some subnet action expression in the vector does not match (by
-    pattern-matching) the corresponding action expression in $C$;
+    pattern-matching) with the corresponding action expression in $C$;
   \item or if the whole set of active subnet actions in the vector
@@
   $S_n \in States(L2_{reach})=States(L2_{sat})$, so $l_n$ will have
-  been checked ``on-the-fly'', in line 6 of Algorithm~\ref{alg3}. Then
+  been checked on the fly, in line 6 of Algorithm~\ref{alg3}. Then
   the transition $S_n \xrightarrow{l_{n}}S$ will be added to $L2_{sat}$, and thus $S \in States(L2_{reach})$.
@@
 
-Here the behavior of the hole ``P'' ($a1$ in Figure~\ref{schema:unsat-ot}) , after matching with the synchronisation vectors, appears as a variable
-``|a1:sva\_SVA0:15:1|'', and ``R'' ($acc(x2)$) as ``|(ACT delta
+Here the behavior of the hole ``$P$'' ($a1$ in Figure~\ref{schema:unsat-ot}), after matching with the synchronisation vectors, appears as a variable
+``|a1:sva\_SVA0:15:1|'', and ``$R$'' ($acc(x2)$) as ``|(ACT delta
 |x:sva\_SV4:1:2|''. Line 16 requires that $a1 = \delta(x2)$ to match
@@
 17-18 that $a1$ does not match $\delta(x1)$ for any $x1$. 
-We also display  the diagnosis (``sat'' or ``unsat'') generated by Z3.
+We also display  the diagnosis (``SAT'' or ``UNSAT'') generated by Z3.
 
@@
 inequality, or a guard. 
-The result (sat or unsat) of the final \texttt{check-sat} command in
+The result (SAT or UNSAT) of the final \texttt{check-sat} command in
 the translation () is then decoded.
@@
 
-\paragraph{Computed open automaton}
+\paragraph{Computed open automaton.}
 
@@
         \medskip
-        In the basic cases (EnableState, EnableData) there is no
-        benefit, and even an overhead in the case of EnableData,
+        In the basic cases ($EnableState$, $EnableData$) there is no
+        benefit, and even an overhead in the case of $EnableData$,
         because of the extra step of checking SAT at the end of the
@@
 states are reachable, these tests show a significant benefit of the ``smart'' strategy, in
-the considered use-cases, with 50\% of time saving for the FailureTimer,
+the considered use-cases, with 50\% of time saving for the $FailureTimer$,
 over to 80\% for the composition, depending
@@
 pNet hierarchical structure. The result is a so-called
-\emph{open automaton}, whose transitions contain predicates relating
+open automaton, whose transitions contain predicates relating
 the actions of the pNet holes and controllers. Some of the open

### 2019-04-02 2016-Weak-FH-Bisim/WeakBisim.tex
proof of lemma 6...

@@
 
-\begin{lemma}[Weak open transition composition]\label{lem-compose} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
+\begin{lemma}[Weak open transition composition]\label{lem-Weakcompose} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
 	Suppose $j_0\in J$ and $\gamma_{j_0}=[\beta_0..\beta_n]$ and additionally:\\[-2ex]
@@
 \end{lemma}
-\TODO{Proof}
+\TODO{Proof starts from here}
 
@@
 
-Note: If $(\beta^i_p)_{j_0}=\tau$ Because of Definition 11, $P$ necessarily do a $\tau$ open transition and remains in the same state, ($s_p = s_{p+1}$).
-Thus without loss of generality, we can bypass such an open transition and obtain another decomposition of the WOT without the open transition that requires $({\beta^i_p})_{j_0}=\tau$.
-We can thus  suppose that for all $p$ and $i$ we have $({\beta^i_p})_{j_0}\neq\tau$.
+Note that if $(\beta^i_p)_{j_0}=\tau$ because of Definition \ref{def:Non-ObsTau}, $P$ necessarily makes a $\tau$ open transition and remains in the same state, ($s_p = s_{p+1}$).
+Thus without loss of generality, we can bypass such an open transition and obtain another decomposition of the WOT without the open transition that requires ${\beta^i_{p{j_0}}}=\tau$.
+We can thus  suppose that for all $p$ and $i$ we have ${\beta^i_{p{j_0}}}\neq\tau$.
 
@@
          {\ostate{s^{i\in L}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L}_{(p+1)i}}}$ 
+At the beginning $Q$ is at state $\ostate{s_{q0}}$. We proceed by iteration over the list  $\gamma_{j_0}=[\beta_0..\beta_n]$.\\
+For each step when $P$ moves, we have two cases:
+\begin{itemize}
+\item If $j_0\in J$ then Q moves by one open transition, and by hypothesis  $\beta^i_{j_0}=\beta_t$ with $\beta^i_{j_0}\neq \tau$ for some $t$ such that $t$ has value $0$ at beginning and that is incremented whenever this condition is satisfied.
+In this case, we have:
+\[Q\models{\openrule
+	{
+		\gamma_{t j}^{j\in J_t},
+		 \Pred_t,  
+		\Post_t}
+	{\ostate{s_{t i}^{i\in L_Q}} \OTWeakarrow {\alpha_t}
+		\ostate{s_{(t+1) i}^{\, i\in L_Q}}}
+}
+\]
+By  Lemma \ref{lem-rel-OT-WOT} we can decompose $\WOT_t$ into  a series of $k+k'$ tau open transitions and the observable open transition:
+
+\[Q\models{\openrule
+	{
+		\gamma_{t j}^{j\in J_t},
+		 \Pred_t,  
+		\Post_t}
+	{\ostate{s_{t i}^{i\in L_Q}} \OTarrow {\alpha_t}
+		\ostate{s_{(t+1) i}^{\, i\in L_Q}}}
+}
+\]
+\begin{enumerate}
+
+\item For the first $k$ open tau transitions, by Definition \ref{def:Non-ObsTau} $P$ can make a tau open transition and the hole makes also tau action.
+So by Lemma \ref{lem-compose} we obtain $k$ open transitions in the form:
+\[P[Q]_{j_0}\!\models		
+\openrule
+    {
+       \beta_p^{(p\in J\setminus\{j_0\}) \uplus J_Q},{\Pred_p},{\Post_p}   }
+         {\ostate{s^{i\in L \uplus L_Q}_{pi}} \OTarrow {\tau} \ostate{s^{i\in L\uplus L_Q }_{(p+1)i}}}\]
+
+\item We proceed in the same way for $k'$ last weak open transitions, and we obtain $k'$ open tau transitions.\\
+\item For the observable open transition. We have $\alpha_t=\beta_{j_0}$  by Lemma \ref{lem-compose} we obtain:\\ 
+\[P[Q]_{j_0}\!\models		
+\openrule
+    {
+       \beta_p^{(p\in J\setminus\{j_0\}) \uplus J_Q},{\Pred_p}\!\!'',{\Post_p}\!\!''   }
+         {\ostate{s^{i\in L \uplus L_Q}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L\uplus L_Q }_{(p+1)i}}}\] \\
+ such that  ${\Pred_p}\!\!'' \iff {\Pred_p}
+		\land {\Pred_p}\!\!'\land \alpha_t=\beta_{j_0}$, ${\Post_p}\!\!''={\Post_p}\uplus 
+		{\Post_p}\!\!'$\\ 
+\end{enumerate}
+
+By Lemma \ref{lem-rel-OT-WOT} from cases $(1)$, $2$ and $(3)$ we obtain: 
+\[P[Q]_{j_0}\!\models		
+\openrule
+    {
+       \beta_p^{(p\in J\setminus\{j_0\}) \uplus J_Q}, {\Pred_p}
+		\land {\Pred_p}\!\!'\land \alpha_p'=\beta_{j_0}$, ${\Post_p}\!\!''={\Post_p}\uplus 
+		{\Post_p}\!\!'}
+         {\ostate{s^{i\in L\uplus L_Q}_{pi}} \OTWeakarrow {\alpha} \ostate{s^{i\in L \uplus L_Q}_{(p+1)i}}}\]
+
+ \item Else, $j_0\not\in J$. $t$ does not move  and $Q$ does not move, i.e. we have: $\ostate{(s_{ti})^{i\in L_Q}} = \ostate{({s}_{(t+1)i})^{i\in L_Q}}$....
+\end{itemize}
+
+---------------------------------------------------------
 

### 2019-04-03 2016-Weak-FH-Bisim/WeakBisim.tex
work pn proof of lemma 6 over skype

@@
 \]
-We can apply Lemma \ref{lem-compose} on each   $\symb{OT}_p$ of $P$ in the form: 
+
+We proceed by iteration on the list of   $\symb{OT}_p$ of $P$ identified above with an additional variable $t$, OTs are of the form: 
 $P\!\models		
@@
     {
-       {(\beta^i_p)^{p\in J}},\Pred_p,\Post_p   }
+       {(\beta^i_{p j})^{j\in J}},\Pred_p,\Post_p   }
          {\ostate{s^{i\in L}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L}_{(p+1)i}}}$ 
-At the beginning $Q$ is at state $\ostate{s_{q0}}$. We proceed by iteration over the list  $\gamma_{j_0}=[\beta_0..\beta_n]$.\\
-For each step when $P$ moves, we have two cases:
+At the beginning $Q$ is at state $\ostate{s_{0}}$ and $t=0$. 
+For each step, we have two cases:
 \begin{itemize}
-\item If $j_0\in J$ then Q moves by one open transition, and by hypothesis  $\beta^i_{j_0}=\beta_t$ with $\beta^i_{j_0}\neq \tau$ for some $t$ such that $t$ has value $0$ at beginning and that is incremented whenever this condition is satisfied.
-In this case, we have:
+\item If $j_0\in J$ then Q moves by one open transition. By the hypothesis above $\beta^i_{j_0}\neq \tau$. Additionally, we have
+$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{p=0}^{m_1} \vis{\set{\beta^1_p}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{p=0}^{m_2} \vis{\set{\beta^3_p}}}$ and\\
+ $\gamma_{j_0}=[\beta_0..\beta_n]$, thus
+  $\beta^i_{j_0}=\beta_t$ with  for some $t$ such that $t$ has value $0$ at beginning and that is incremented whenever this condition is satisfied.
+
+On the other hand, by hypothesis we have:
 \[Q\models{\openrule
@@
 		\Post_t}
-	{\ostate{s_{t i}^{i\in L_Q}} \OTWeakarrow {\alpha_t}
-		\ostate{s_{(t+1) i}^{\, i\in L_Q}}}
+	{ \ostate{s_{t}}\OTWeakarrow {\alpha_t}
+		\ostate{s_{{(t+1)}}}}
 }
@@
 		\Post_t}
-	{\ostate{s_{t i}^{i\in L_Q}} \OTarrow {\alpha_t}
-		\ostate{s_{(t+1) i}^{\, i\in L_Q}}}
+	{\ostate{s^2_{t}}\OTarrow {\alpha_t}
+		\ostate{s^3_{t}}}
 }
@@
 \item We proceed in the same way for $k'$ last weak open transitions, and we obtain $k'$ open tau transitions.\\
-\item For the observable open transition. We have $\alpha_t=\beta_{j_0}$  by Lemma \ref{lem-compose} we obtain:\\ 
+\item For the observable open transition.
+Because of the definition of $\Pred'$ we can suppose that $\alpha_t=\beta_{j_0}$ \TODO{because else the original WOT does not trigger}.
+By Lemma \ref{lem-compose} we obtain:\\
 \[P[Q]_{j_0}\!\models		

### 2019-04-09 2016-Weak-FH-Bisim/WeakBisim.tex
biblio, TODOs, removed \I et def 11 corrigee

@@
 \paragraph{Previous Works and Contribution}
-While most of our previous works relied on closed, fully-instantiated semantics~\cite{BBCHM:article2009,AmeurBoulifa2017,HKM-FASE16}, it is only recently that we could design a first version of a  parameterised semantics for pNets with a strong bisimulation equivalence~\cite{henrio:Forte2016}.
+While most of our previous works relied on closed, fully-instantiated semantics~\cite{BBCHM:article2008,AmeurBoulifa2017,HKM-FASE16}, it is only recently that we could design a first version of a  parameterised semantics for pNets with a strong bisimulation equivalence~\cite{henrio:Forte2016}.
 This article builds open this previous parameterised semantics and provide a cleaner version of the semantics with a slightly simplified formalism and extends it to deal with weak bisimulation.
@@
 %\def\Actionalg{\mathcal{A}}
-\TODO{Attention: la notation of term algebra is the same for set of transition.}
 
@@
 \begin{itemize}
-\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets indexed over $I \in \I$.
+\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets indexed over $I$.
 %  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which sub-pNets are indexed.
 
-\item[$\bullet$] $J\!\in\!\I_\P$ is a set of indexes, called \emph{holes}.
+\item[$\bullet$] $J$ is a set of indexes, called \emph{holes}.
 $I$ and $J$ are \emph{disjoint}: $I\!\cap\! J=\emptyset$,  $I\!\cup\! J\neq\emptyset$
@@
 \item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
-  synchronisation vectors ($K\in\I_\P$). $\forall k\!\in\! K,
+  synchronisation vectors. $\forall k\!\in\! K,
   \symb{SV}_k\!=\!\SV{\alpha_{l}^{l\in I_k \uplus J_k}}{\alpha'_k}{e_k}$ where
@@
 
-\subsection{Computing and using open automata}
-\TODO{REMOVE?  published at Avocs, we can shorten and add a bibref}
-In this section we present a simple algorithm to construct the open
-automaton representing the behaviour of an open pNet, and we prove that
-under reasonable conditions this automaton is finite.
-
-\begin{algorithm}[Behavioural semantics of open pNets: Sketch]
-This is a standard residual algorithm over a set of open-automaton
-states, but where transitions are open transitions
-constructively ``proven'' by deduction trees.
-
-1) Start with a set of unexplored states containing the initial state
-of the automaton, and an empty set of explored states.
-
-2) While there are unexplored states, pick one state from the
-unexplored set and add it to the explored set.
-
-2a- From this state
-build all possible deduction trees by application of the structural
-rules \TrUn\ and \TrDeux, using all applicable combinations
-of synchronisation vectors.
-In practice, the algorithm does not explicitely construct the
-deduction tree, but for each pNet node, builds all possible
-combinations of the OTs of its subnets, and filter these combinations
-by matching with all synchronisation vectors.
-
-2b- For each OT built, add the transition in the
-outgoing transitions of the current state, and add the
-resulting state in the unexplored set if it is not already there.
-
-3) The predicate is submitted to Z3 for checking satisfiability. If it
-is NOT satisfiable, the resulting OT is discarded. This will minimize
-the number of resulting transitions, and by reachability analysis,
-reduce the resulting open automaton.
-
-\end{algorithm}
+%\subsection{Computing and using open automata}
+%\TODO{REMOVE?  published at Avocs, we can shorten and add a bibref}
+%In this section we present a simple algorithm to construct the open
+%automaton representing the behaviour of an open pNet, and we prove that
+%under reasonable conditions this automaton is finite.
+%
+%\begin{algorithm}[Behavioural semantics of open pNets: Sketch]
+%This is a standard residual algorithm over a set of open-automaton
+%states, but where transitions are open transitions
+%constructively ``proven'' by deduction trees.
+%
+%1) Start with a set of unexplored states containing the initial state
+%of the automaton, and an empty set of explored states.
+%
+%2) While there are unexplored states, pick one state from the
+%unexplored set and add it to the explored set.
+%
+%2a- From this state
+%build all possible deduction trees by application of the structural
+%rules \TrUn\ and \TrDeux, using all applicable combinations
+%of synchronisation vectors.
+%In practice, the algorithm does not explicitely construct the
+%deduction tree, but for each pNet node, builds all possible
+%combinations of the OTs of its subnets, and filter these combinations
+%by matching with all synchronisation vectors. 
+% 
+%2b- For each OT built, add the transition in the
+%outgoing transitions of the current state, and add the
+%resulting state in the unexplored set if it is not already there.
+%
+%3) The predicate is submitted to Z3 for checking satisfiability. If it
+%is NOT satisfiable, the resulting OT is discarded. This will minimize
+%the number of resulting transitions, and by reachability analysis,
+%reduce the resulting open automaton.
+%
+%\end{algorithm}
 
@@
 holes, and each pLTS at leaves having a finite number of states and
-(symbolic) transitions, has a finite automaton (see \ref{henrio:Forte2016}).
+(symbolic) transitions, has a finite automaton (see \cite{henrio:Forte2016}). The algorithm for building such an automaton can be found in~\cite{QBMZ-AVOCS18}.
 
@@
 This theorem is quite powerful somehow states that the theory of open pNets is convenient to study properties of process composition.
-Open pNets can indeed be used to study process operators and process algebras, as shown in~\cite{henrio:Forte2016}, or to study interaction protocols \TODO{ref vers fault tolerance byzantine FACS 2011}
+Open pNets can indeed be used to study process operators and process algebras, as shown in~\cite{henrio:Forte2016}, or to study interaction protocols~\cite{BHHM:FACS11}.
 
@@
 and 
-\item for all $\alpha$, $j$, $s$, $\Post$ and $s'$ such that
+\item for all $A$, $\alpha$,  $s$, $\Post$ and $s'$ such that
 \[ \openrule
          {
-           (j\mapsto\tau),\Pred,\Post}
+           A,\Pred,\Post}
          {s \OTarrow {\alpha} s'}
-         \in \mathcal{T} \] we have \[ \alpha=\tau\land s=s'\land \Pred=\True\land\Post=\Id(s)
+         \in \mathcal{T} \] If there is a $j$ such that $A(j)=\tau$ then we have \[ \alpha=\tau\land s=s'\land \Pred=\True\land\Post=\Id(s)
 \]
-\TODO{question : it looks like we can have 2 holes doing a tau and observe this ; I belive this is not safe TODO LUDO add a $A(j)=\tau$}
 \end{enumerate}
@@
 
-\begin{property}[pNets that cannot observe silent actions]
+\begin{property}[Non-observability of silent actions]
 The open semantics of a pNets that cannot observe silent actions is an open automaton that  cannot observe silent actions.
@@
 
-\TODO{question : we could merge prop 1 and def above, is it better?}
+%\TODO{question : we could merge prop 1 and def above, is it better?}
 

### 2019-04-09 2017-Xudong-SMT/ActaInformatica.tex
Redone proof 3

@@
 \State $\mathit{L1}$=filterUnsatTransitions($\mathit{L,Assignments}$);
-\State $\mathit{OA_0}$=makeReachableSubAutomaton($\mathit{InitState}(P),L1)$;
-\Repeat $\mathit{OA_n}$=RefineReachableSubAutomaton($\mathit{OA_{n-1}}$)
-\Until  $\mathit{OA_n}=\mathit{OA_{n-1}}$;   \hfill $\setminus \setminus$ Fixed point reached
-\State \Return $\mathit{OA_n}$;
+\State $\mathit{OA_1^0}$=makeReachableSubAutomaton($\mathit{InitState}(P),L1)$;
+\Repeat $\mathit{OA_1^n}$=RefineReachableSubAutomaton($\mathit{OA_1^{n-1}}$)
+\Until  $\mathit{OA_1^n}=\mathit{OA_1^{n-1}}$;   \hfill $\setminus \setminus$ Fixed point reached
+\State \Return $\mathit{OA_1^n}$;
 
@@
 unexplored set, until this set is empty.
-
-Before the SAT checking step, it may contain symbolic transitions that
-do not have valid ground instantiations. This is not logically
-incorrect, but is naturally not an optimal representation. So we prune
-these UNSAT transitions: at the end of the open automaton generation,
-the predicate of each OT is translated 
-into SMTlib assertions (see Section~\ref{section:pruning}), and checked for
-satisfiability (function \texttt{filterUnsatTransitions}). 
-Then we compute the set of reachable transitions and states to build
-the final open automaton (more details in Section~\ref{section:BuildingTheOpenAutomaton}).
 
@@
 holes of the node, so \emph{MakeTransitions} is never called on a hole.
+
+Before the SAT checking step, the set $L$ may contain symbolic transitions that
+do not have valid ground instantiations. This is not logically
+incorrect, but is naturally not an optimal representation. So (line 11) we prune
+these UNSAT transitions: at the end of the open automaton generation,
+the predicate of each OT is translated 
+into SMTlib assertions (see Section~\ref{section:pruning}), and checked for
+satisfiability (function \texttt{filterUnsatTransitions}). 
+Then we compute (lines 12-14) the set of reachable transitions and states to build
+the final open automaton (more details in Section~\ref{section:BuildingTheOpenAutomaton}).
 
@@
 transitions and states), by checking the predicates for satisfiability.
-In Figure~\ref{schema:unsat-ot}, we show an 
-unsatisfiable open transition 
-from the open automaton of our running example.
-
-It shows the case where processes $P$ and $R$ ``try'' to communicate directly, but this is made impossible by the combination of chosen synchronisation vectors and their guards. This
-  mismatch is materialised by the predicate
-fragment ``$a1 = \delta(x2) \land \forall z. a1 \neq \delta(z)$''. In Section~\ref{section:TranslationToSMTlib} we will show how this is encoded and checked using the SMT engine.
-
-\begin{figure}[h]
+
+\begin{example}[Unsat OT]
+  \label{schema:unsat-ot}
 \begin{mathpar}
@@
 	\end{mathpar}
-\caption{One of the unsatisfiable open transitions}  \label{schema:unsat-ot}
-\end{figure}
+
+Here we display an  
+unsatisfiable open transition 
+from the open automaton of our running example.
+It shows the case where processes $P$ and $R$ ``try'' to communicate directly, but this is made impossible by the combination of chosen synchronisation vectors and their guards. This
+  mismatch is materialised by the predicate
+fragment ``$a1 = \delta(x2) \land \forall z. a1 \neq \delta(z)$''. In Section~\ref{section:TranslationToSMTlib} we will show how this is encoded and checked using the SMT engine.
+\end{example}
 
@@
 The ``Modulo Theory'' part of SMT solvers is important here, as
-the solvers can use specific properties of each action algebra.
+the solvers can use specific properties of each data type in the action algebra.
 
@@
 satisfiability checking, for all the OTs computed that far.
+For a transition
+\[		\inferrule*[myfraction=\reddottedrule]
+		{%\{s_i~{\xrightarrow{a_i}}_i ~s_i^{\prime}\}^{i\in I},
+			\{\xrightarrow{\beta_j}_j\}^{j\in J}, \Pred\,, \Post}
+		{s \xrightarrow {\alpha}s'}
+                \]
+                we need to build a predicate encoding both the OT predicate, and
+the information available on the possible assignments of the initial
+state $s$. This is expressed as
+\[Pred_{l}\wedge \bigwedge_{v\in vars(s)}\{ \bigvee_{Assign\in
+  assigns(v,s)} Assign\}
+\]
+where each $Assign$ represents one of the possible (symbolic) value of
+variable the state variable $v$.
 
@@
 
-The set $L1$ may contain unreachable transitions. To remove those transitions, the last step of the
-algorithm builds the final open automaton via a traversal of $L1$,
+The set $L1$ may contain unreachable transitions. To remove those
+transitions, the last step of the  
+algorithm (lines 12-14) builds the final open automaton via a traversal of $L1$,
 starting at the initial state $InitState(p)$ as defined in
@@
 assignments of the corresponding target states. In
-Algorithm~\ref{alg1}, we iterate this procedure, each iteration
+Algorithm~\ref{alg1}, we iterate this procedure (lines 13-14), each iteration
 reducing the set of 
@@
 (e.g. model-checking or equivalence checking) will be able to use the
-full information from the predicates and the assignment sets.
+full information from the predicates and the assignment sets, even if
+some spurious OTs are left here.
 
@@
   transitions, reachability is not as easy to define as in standard
-  models, as illustrated by the definition above. By avoiding building
+  models, as illustrated by the discussion above. By avoiding building
   the OTs coming from some unreachable states, we also avoid adding
@@
 the reachable state space and assignment sets; this corresponds to
-the automaton $OA_0$ in Algorithm~\ref{alg3}, line 15.
+the automaton $OA_2^0$ in Algorithm~\ref{alg3}, line 13.
 So the smart algorithm proceeds in two steps: during the
 first step, the SAT checking is done without using any assignment set
-information. Then after the completion of this step, we refine the
-reachability computation, using the
-assignment information as described in the previous section.
+information (line 5).  Only the OTs found SAT from this check will be added
+to $L$, and the corresponding target global state added to $U$ if
+necessary. This ensures that all explored global states are
+effectively reachable by a chain of SAT OTs.
 
@@
 \State $\mathit{L2}$=filterUnsatTransitions($\mathit{L,Assignments}$);
-\State $\mathit{OA_0}$=makeReachableSubAutomaton($\mathit{InitState}(P),L2)$;
-\Repeat $\mathit{OA_n}$=RefineReachableSubAutomaton($\mathit{OA_{n-1}}$)
-\Until  $\mathit{OA_n}=\mathit{OA_{n-1}}$;
-\State \Return $\mathit{OA_n}$;
+\State $\mathit{OA_2^0}$=makeReachableSubAutomaton($\mathit{InitState}(P),L2)$;
+\Repeat $\mathit{OA_2^n}$=RefineReachableSubAutomaton($\mathit{OA_2^{n-1}}$)
+\Until  $\mathit{OA_2^n}=\mathit{OA_2^{n-1}}$;
+\State \Return $\mathit{OA_2^n}$;
 %\EndIf
@@
 
-Algorithm~\ref{alg3} implements this new stategy: in line 5, it runs
-the satisfiability check on each OT generated from this global
-state. This check is done without using the assignment information, as
-discussed above. Only the OTs found SAT from this check will be added
-to $L$, and the corresponding target global state added to $U$ if
-necessary. This ensures that all explored global states are
-effectively reachable by a chain of SAT OTs.
-
 At the end of the residual loop, we do another traversal of the
 automaton, this time using the assignment information collected that
-far, and compute the final reachable sub-automaton. 
+far (line 12), and compute the final reachable sub-automaton
+iteratively (lines 13-15), in the same way than in algorithm \ref{alg1}. 
 Naturally, this step is only useful if there are some assignments.
+
+\medskip
+Now we will prove that the smart algorithm computes the same 
+open automaton.
 
@@
 the open automaton needs not to collect the set of possible values dealing
-with the values of local variables, so we can directly compute the
-reachable part of the automaton using the on-the-fly algorithm (line 13).
+with the values of local variables, so the final automaton is $AO_2^0$ as
+computed in line 13.
 
@@
 
-% \ERIC{Sketch of the proof:}
-
-%    \medskip
-%  \noteInEM{I keep below the original proof draft from Xudong, though
-%    I'm not sure if parts of it can be reused}
 \begin{proof}[Theorem \ref{Th:CorrectnessWithoutAssignments}]
@@
     \item $L1_{reach}$: the final set of OTs of Algorithm~\ref{alg1}, as computed
-      by line 12 (as $OA_0$). Without assignments the following
+      by line 12 (as $OA_1^0$). Without assignments the following
       refinement step will do nothing, the fixpoint is already reached.
@@
     \item $L2_{reach}$: the final set of OTs of Algorithm~\ref{alg3}, as computed
-          by line 13. Here also $OA_n = OA_0$.
+          by line 13. Here also $OA_2^n = OA_2^0$.
    \item $States: \overline{OT}\rightarrow\overline{State}$:  the function that
 computes the set of target states of a set of OTs.  
-  \item $Rename:  L1_{reach} \rightarrow L2_{reach}$:  a function that keeps state names of transitions but renames fresh variables in the transition labels.
+  \item $Rename:  L1_{reach} \rightarrow L2_{reach}$:  a function that
+    keeps state names of transitions but renames fresh variables in
+    the transition labels. In the sequel, transitions $l_i$ will range
+    over $L0$ set (and $L1_*$), and $l'_i$ will range over $L2_*$
+    sets. Of course renaming preserves satisfiability.
 \end{itemize}
 
-%% When the pNets contains no assignment, there is no need for the last
-%% filtering step, so $L1_{sat}=L1_{reach}$ and $L2_{sat}=L2_{reach}$.
-
 \smallskip
-We now prove that $L1_{reach}=L2_{reach}$, which will imply
-the equality of the two open automata.
+We now prove that $L1_{reach}=L2_{reach}$ and
+$States(L1_{reach})=States(L2_{reach})$.
+
+By definition of the algorithms, we have:
+
+\centerline{$L1_{reach} \subseteq L1_{sat} \subseteq L0$}
+\centerline{$L2_{reach}\subseteq  L2_{sat}$}
 
@@
 Algorithm~\ref{alg3} computes fewer transitions than
-Algorithm~\ref{alg1}. Formally, we have that $L2_{reach}\subseteq  L2_{sat} \subseteq L0$, and as a consequence $States(L2_{reach})\subseteq  States(L0)$, i.e.,\\
+Algorithm~\ref{alg1}. Formally, we have that
+$L2_{sat} \subseteq Rename(L0)$ (up to renaming of fresh variables), and as a consequence $States(L2_{reach})\subseteq  States(L0)$, i.e.,\\
 \centerline{$\forall \ostate{\overline{u}}\in States(L2_{reach}), \exists\ostate{\overline{t}}\in States(L0), \ostate{\overline{t}}=\ostate{\overline{u}}$}
@@
   suppose $|S|_{L2_{reach}}=n+1$, then there exists a chain
-  $S_0\xrightarrow{l_1}S_1\xrightarrow{l_2}...S_{n}\xrightarrow{l_{n+1}}S$
-  with all $l_k \in L2_{reach}$. In particular, since
-  $L2_{reach}\subseteq L2_{sat}$, we have that $l_{n+1} \in L2_{sat}$ and
+  $S_0\xrightarrow{l'_1}S_1\xrightarrow{l'_2}...S_{n}\xrightarrow{l'_{n+1}}S$
+  with all $l'_k \in L2_{reach}$. In particular, since
+  $L2_{reach}\subseteq L2_{sat}$, we have that $l'_{n+1} \in L2_{sat}$ and
   its predicate is satisfiable.
@@
   By induction hypothesis, we get $S_{n} \in States(L1_{reach})$, so during the
-  call of $makeReachableSubAutomaton$ in Algorithm~\ref{alg1}, line 12, the OT
-  $S_n \xrightarrow{l_{n}}S$ will be checked and found SAT, so
+  call of $makeReachableSubAutomaton$ in Algorithm~\ref{alg1}, line
+  12, there exists an OT
+  $S_n \xrightarrow{l_{n}}S$ in $L1_{sat}$, with $l'_n=Rename(l_n)$;
+  this OT will be checked and found SAT, so
   $S \in States(L1_{reach})$.
@@
   States(L1_{reach})$ and $l_n$ is satisfiable. By induction, we have
-  $S_n \in States(L2_{reach})=States(L2_{sat})$, so $l_n$ will have
+  $S_n \in States(L2_{reach})=States(L2_{sat})$, so there exists
+  $l'_n=Rename(L_n)$ that will have
   been checked on the fly, in line 6 of Algorithm~\ref{alg3}. Then
-  the transition $S_n \xrightarrow{l_{n}}S$ will be added to $L2_{sat}$, and thus $S \in States(L2_{reach})$.
-
-Note that $L0$ is finite, so we conclude $L1_{reach}=L2_{reach}$, and $States(L1_{reach})=States(L2_{reach})$.
+  the transition $S_n \xrightarrow{l'_{n}}S$ will be added to
+  $L2_{sat}$, and thus $S \in States(L2_{reach})$.
+
+Note that $L0$ is finite, so we conclude $L1_{reach}=L2_{reach}$, and
+$States(L1_{reach})=States(L2_{reach})$.
 
@@
   checking. Still, the smart strategy will explore a reduced state
-  space, not necessarily the minimal one. In the
+  space, though not necessarily the minimal one. In the
   following theorem, both algorithms are considered in their complete
@@
 \begin{proof}
-  Define the OT sets $L0, L1_{sat}, L2_{sat}, L2_{reach}$ and the function $States$ as in the proof of Theorem~\ref{Th:CorrectnessWithoutAssignments}, and
+  Define the OT sets $L0, L1_{sat}, L2_{sat}, L2_{reach}$ and the
+  function $States$ as before, and:
 
   \begin{itemize}
-    \item $L1_{reach*}$: the final set of OTs of Algorithm~\ref{alg1}, as computed
+    \item $L_1^*$: the final set of OTs of Algorithm~\ref{alg1}, as computed
         by an iterative application of $makeReachableSubAutomaton$ (line
         14) up to a  fixed point.
-      \item $L2_{reach*}$: the final set of OTs of Algorithm~\ref{alg3}, as computed
+    \item $L_2^*$: the final set of OTs of Algorithm~\ref{alg3}, as computed
         by an iterative application of $makeReachableSubAutomaton$ (line
-        16) up to a fixed point.
-        \item $Assignments : \overline{OT}\ \times State\rightarrow \overline{Assign}$: the function of
-        computing the set of assignments of a global state from a given set of OTs.
+        15) up to a fixed point.
+    \item $Assigns : \overline{OT}\ \rightarrow \overline{Assign}$: the function
+          of computing the set of assignments of (the variables of the
+          states of) a given set of OTs.
+    \item $Assigns : \overline{OT}, Vars\ \rightarrow \overline{Assign}$: similarily,
+      but for assignments concerning one specific state variable.
   \end{itemize}
@@
 \smallskip
-The structure implicitly computed by both algorithms is a triple $ Aut= \langle \overline{OT}, \overline{State},\\ \overline{Assign}\rangle$.
-The assignments set of $OA_1$ is $\{Assignments(L1, S_i)\}^{S_i\in States(L1)}$ and that of $OA_2$ is $\{Assignments(L2_{sat}, S_j)\}^{S_j\in States(L2_{sat})}$. The result triples are:  
-\noindent
+The structure implicitly computed by both algorithms is a triple
+$Aut= \langle \overline{OT},\overline{State},\\ \overline{Assign}\rangle$.
+
+We already know that $L2_{sat}\subseteq L1_{sat}$ (up to renaming),
+because every OT that will be checked positively (using assignments) in line 12 of
+algorithm \ref{alg3} will also be tested by algorithm \ref{alg1} (as
+$L2_{sat}\subseteq L0$), and with a larger set of assignments.
+
+Consequently the initial triples of the refinement loop are:
+
 \begin{align*}
-Aut_1 = \langle L1_{sat}, States(L1_{sat}), \{Assignments(L1, S_i)\}^{S_i\in States(L1)}\rangle\ , \\
-Aut_2 = \langle L2_{sat}, States(L2_{sat}), \{Assignments(L2_{sat}, S_j)\}^{S_j\in States(L2_{sat})}\rangle \  .
+Aut_1^0 = \langle L1_{sat}, States(L1_{sat}), Assigns(L1_{sat})\rangle \\
+Aut_2^0 = \langle L2_{sat}, States(L2_{sat}), Assigns(L2_{sat})\rangle \\
+\text{with } Aut_2^0 \subseteq Aut_1^0, \text{ component-wise and up to renaming.}
 \end{align*}
 
-Based on this triple structure, we define the function $Refine : Aut \rightarrow Aut$ modelling $makeReachableSubAutomaton(S0,OTs)$.
-It uses the assignments of the previous step to refine the computed reachable space:
+%% The assignments set of $OA_1^0$ is $\{Assigns(L1, States(L1))\}$ and
+%% that of $OA_2^0$ is $\{Assigns(L2_{sat}, States(L2_{sat}))}\}$. The
+%%   result triples are:    
+%% \noindent
+%% \begin{align*}
+%% Aut_1 = \langle L1_{sat}, States(L1_{sat}), \{Assignments(L1, S_i)\}^{S_i\in States(L1)}\rangle\ , \\
+%% Aut_2 = \langle L2_{sat}, States(L2_{sat}), \{Assignments(L2_{sat}, S_j)\}^{S_j\in States(L2_{sat})}\rangle \  .
+%% \end{align*}
+
+Based on this triple structure, we define the function $Refine : Aut
+\rightarrow Aut$ modelling the function $makeReachableSubAutomaton(S0,OTs)$. It
+uses the assignments of the OTs remaining from the previous iteration
+to refine the computed reachable space: 
 \begin{align*}
-Refine(Aut) &=\langle L', States(L'), \{Assignments(L', S_i)\}^{S_i\in States(L')}\rangle \\
-&=Aut'
+Aut^n = Refine(Aut^{n-1}) &=\langle L^n, States(L^n), Assigns(L^n)\rangle
 \end{align*}
-where $L' = L - L_{unsat}$, and $L_{unsat}$ is the set of unsatisfiable transitions checked in this iteration.
-We have $L'\subseteq L$, and potentially, their target states and corresponding assignments may be reduced:
-\[States_{L'}=\{S_0\}\cup \bigcup States(L'),\]
-\[Assignments_{L',States_{L'}}=\bigcup\{Assignments(L', State_{i})\}^{State_{i}\in States_{L'}} \]
-\[s.t. |States_{L'}|\le|States_{L}|\wedge|Assignments_{L',States_{L'}}|\le|Assignments_{L,States_{L}}|.\]
-
-In one single iteration, the satisfiability of a transition $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L$ is checked through whether 
-\[\bigvee_{Assign_i\in Assignments_{L, States_{L}}}(Pred_{l}\wedge Assign_{i})\text{ is true}.\]
-More transitions could become unsatisfiable after the reduction of the assignments set, so the function needs to be iterated several times.
-In each iteration, the number of triples decreases, thus there exists a sequence \[Aut^n = Refine(Aut^{n-1})\quad s.t.
-|Aut^n| < |Aut^{n-1}|.\]
-The iteration terminates if $Aut''$ contains no more unsatisfiable transition, then there is a fixed point $Aut'' = Refine(Aut'')$ and $|Aut''| = |Refine(Aut'')|$.
-
-Let $Aut''_1$ and $Aut''_2$ be two fixed points with $Refine(Aut''_1) = Aut''_1$ and $Refine(Aut''_2) = Aut''_2$.
-Focusing on the transition sets in $Aut''_1$ and $Aut''_2$, $L1''_{sat}=L1_{reach}$ and $L2''_{sat}=L2_{reach}$, we need to check their equivalence.
-
-First, there is an inclusion relation between the initial assignments sets, 
-\begin{align*}
-&L2_{sat}\subseteq L1\Rightarrow States_{L2_{sat}}\subseteq State_{L1}\\
-\Rightarrow &Assignments_{L2_{sat}, States_{L2_{sat}}}\subseteq Assignments_{L1, States_{L1}}
-\end{align*}
-
-Then we come to see what changes have occurred during the iterations.
+where $L^n = Reach(L^{n-1} - L^{n-1}_{unsat})$, and $L^{n-1}_{unsat}$ is the
+set of unsatisfiable transitions checked in this iteration. We have
+$L^n\subseteq L^{n-1}$, and consequently, their states and assignments
+may be reduced:
+$States(L^n)\subseteq States(L^{n-1}) \land Assigns(L^n)\subseteq
+Assigns(L^{n-1})$.
+
+%% \[States_{L'}=\{S_0\}\cup \bigcup States(L'),\]
+%% \[Assignments_{L',States_{L'}}=\bigcup\{Assignments(L', State_{i})\}^{State_{i}\in States_{L'}} \]
+%% \[s.t. |States_{L'}|\le|States_{L}|\wedge|Assignments_{L',States_{L'}}|\le|Assignments_{L,States_{L}}|.\]
+
+\smallskip
+In each iteration $k$, consider a transition $l \in L^k$, define
+
+\[Pred(l,L^{k-1}) = Pred_{l}\wedge \bigwedge_{v\in vars(pn)}\{ \bigvee_{Assign\in
+  Assigns(v,L^{k-1})} Assign\}\]
+
+Checking satisfiability of $l$ means checking satifiability of
+$Pred(l,L^{k-1})$.
+
+%% \noteInEM{Xudong: Previous version looks wrong to me, because the
+%%   disjunction is between the various possible assignments of each
+%%   state var, but then you need the conjunction of the information for
+%%   all considered vars:
+%% \[\bigvee_{Assign_i\in Assignments_{L, States_{L}}}(Pred_{l}\wedge
+%% Assign_{i})\text{ is true}.\]}
+
+Note that this is equivalent to the predicate defined in section
+\ref{section:pruning}, because we consider all states variables of the
+pNet, rather than those of state $s$, but assignments
+of other variables will not change the satisfiability.
+
+There are two reasons why an OT would disappear during one application
+of $Aut^k = Refine(Aut^{k-1})$: either its predicate, checked with the set of
+$Assign(L^{k-1})$, became Unsat; or this OT is at
+the end of a sequence starting from a state in $s_0\ \in State(L^k)$,
+the next OT became Unsat, and the following states in the sequence are
+not reachable using satisfiable OTs in $Aut^k$. More formaly, there is a chain
+\[s_0\xrightarrow{ot_1}s_1\xrightarrow{ot_2}...s_{n}\xrightarrow{ot_{n+1}}s_{n+1}\]
+with $Pred(ot_1,L^{k-1})$ Unsat, and all states $s_i, i \in [1..n]$
+unreachable in $Aut^k$.
+
+\smallskip
+In each iteration, the number of triples may decrease, thus there
+exists a sequence \[Aut^n = Refine(Aut^{n-1})\quad s.t. |Aut^n| <
+|Aut^{n-1}|.\]
+The iteration terminates when $Aut^n$ contains no more unsatisfiable
+transition, reaching the fixed point $Aut^n = Refine(Aut^{n-1})$. The
+initial structure is finite by theorem \ref{Th:finiteness}, so the
+iteration always terminates.
+
+\medskip
+Now we prove that the triples at the end of the fixpoint computation
+in both algorithms are equal.
+Let $Aut^*_1$ and $Aut^*_2$ be two fixed points with $Refine(Aut^*_1) =
+Aut^*_1$ and $Refine(Aut^*_2) = Aut^*_2$.  
+We want to prove $L_1^* = L_2^*$.
+
+We already have $Aut_2^0\ \subseteq Aut_1^0$.
+We will prove in 2 steps:
+first prove by induction that $Hyp^k = (L_2^k\ \subseteq L_1^k)$ is
+preserved by application of $Refine$ (meaning that the refine function
+in algorithm 1 cannot go ``faster'' than in algorithm 3), then prove
+that when the fix-points are reached, then they are the same.
+
+Suppose $Hyp^{k-1}$, and prove $Hyp^k$.
+Consider an OT $l\ \in L_2^k$, but $l\ \notin L_1^k$.
+We have \[ l\ \in L_2^k \implies l\ \in L_2^{k-1} \implies l\ \in
+L_1^{k-1}\] so the transtion $l$ has been removed from $L_1^{k-1}$ during the last
+iteration $Refine_1^k$. This can be caused by:
+\begin{itemize}
+\item
+  either $Pred(l,L_1^{k-1})$ is Unsat, because of some assignment
+    $u \in Assigns(L_1^{k-1})$. But $l \in L_2^k$, so its predicate
+    $Pred(l,L_2^{k-1})$ is satisfiable; this is a contradiction,
+    because $Assigns(L_2^k) \subseteq Assigns(L_1^k)$ (having
+    more possible assignments cannot reduce satisfiability).
+  \item
+    or there is a sequence
+    $s_0\xrightarrow{l_1}s_1\xrightarrow{l_2}...s_{n}\xrightarrow{l}s_{n+1}$,
+    with $s_0 \in States(L_1^{k-1})$, $Pred(l_1,L_1^{k-1})$ is Unsat, and
+    all further states unreachable in $L_1^{k-1}$. But as in the
+    previous case, we would have $l_1$ in $L_2^k$ and not in $L_1^k$,
+    reaching a similar contradiction.
+\end{itemize}
+
+\smallskip
+Now consider the fixpoints of the $Refine$ iterations. From the
+initial inclusion $L_2^0\ \subseteq L_1^0$, and our invariant, we get
+inclusion of the fixpoints $L_2^*\ \subseteq L_1^*$.
+
+Suppose there exists an OT $l$ in $L_1^*$ that is not in $L_2^*$. This
+means that $Pred(l,Assigns(L_1^*))$ is satisfiable, but
+$Pred(l,L_2^*)$ is satisfiable, that is a contradiction; or as in the
+invariant proof, there is a similar sequence, with an OT $l_1$
+bringing the contradiction.
+
+So we conclude $L_2^* = L_1^*$
+
+%% First, there is an inclusion relation between the initial assignments sets, 
+%% \begin{align*}
+%% &L2_{sat}\subseteq L1\Rightarrow States_{L2_{sat}}\subseteq State_{L1}\\
+%% \Rightarrow &Assignments_{L2_{sat}, States_{L2_{sat}}}\subseteq Assignments_{L1, States_{L1}}
+%% \end{align*}
+
+%% Then we come to see what changes have occurred during the iterations.
 In the first iteration, the inclusion relation between their assignments implies an inclusion relation of unsatisfiable transitions.
-If there are two transitions $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}} \in L1_{unsat}$ and $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}} \in L2_{unsat},$ then
-\begin{align*}
-&\bigvee_{Assign_i\in Assignments_{L1, States_{L1}}} (Pred_{l}\wedge Assign_i)\text{ is false}\\
-\text{implies }&\bigvee_{Assign_j\in Assignments_{L2_{sat}, States_{L2_{sat}}}} (Pred_{l}\wedge Assign_j)\text{ is false}.
-\end{align*}
-From the relation $\forall\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}} \in L1_{unsat},\exists\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}} \in L2_{unsat}$, it can be implied that $L1_{unsat}\subseteq L2_{unsat}.$
-
-However, its reverse direction is not fulfilled. Recall that $L1_{sat}=L2_{sat}$, more inclusion relations of the assignments can be implied,
-\begin{align*}
-Assignments_{L1, States_{L1}}&\supseteq Assignments_{L2_{sat}, States_{L2_{sat}}}\\
-&\supseteq Assignments_{L1_{sat}-L1_{unsat}, States_{(L1_{sat}-L1_{unsat})}}\\
-&\supseteq Assignments_{L2_{sat}-L2_{unsat}, States_{(L2_{sat}-L2_{unsat})}}
-\end{align*}
-
-Let $L1'_{sat}=L1_{sat}-L1_{unsat}$ and $L2'_{sat}=L2_{sat}-L2_{unsat}$
-Then in the next iteration, the unsatisfiable transition $\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L1'_{unsat}$ removed from $L1'_{sat}$ has two cases, we use $L1'_{unsat1}$ and $L1'_{unsat2}$ where $L1'_{unsat1}+L1'_{unsat2}=L1'_{unsat}$ to present them.
+If there are two transitions $s\xrightarrow{l}s' \in L1_{unsat}$ and $s\xrightarrow{l}s' \in L2_{unsat},$ then
+%% \begin{align*}
+%% &\bigvee_{Assign_i\in Assignments_{L1, States_{L1}}} (Pred_{l}\wedge Assign_i)\text{ is false}\\
+%% \text{implies }&\bigvee_{Assign_j\in Assignments_{L2_{sat}, States_{L2_{sat}}}} (Pred_{l}\wedge Assign_j)\text{ is false}.
+%% \end{align*}
+%% From the relation $\forall s\xrightarrow{l}s' \in L1_{unsat},\exists s\xrightarrow{l}s' \in L2_{unsat}$, it can be implied that $L1_{unsat}\subseteq L2_{unsat}.$
+
+%% However, its reverse direction is not fulfilled. Recall that $L1_{sat}=L2_{sat}$, more inclusion relations of the assignments can be implied,
+%% \begin{align*}
+%% Assignments_{L1, States_{L1}}&\supseteq Assignments_{L2_{sat}, States_{L2_{sat}}}\\
+%% &\supseteq Assignments_{L1_{sat}-L1_{unsat}, States_{(L1_{sat}-L1_{unsat})}}\\
+%% &\supseteq Assignments_{L2_{sat}-L2_{unsat}, States_{(L2_{sat}-L2_{unsat})}}
+%% \end{align*}
+
+%% Let $L1'_{sat}=L1_{sat}-L1_{unsat}$ and $L2'_{sat}=L2_{sat}-L2_{unsat}$
+%% Then in the next iteration, the unsatisfiable transition $s\xrightarrow{l}s'\in L1'_{unsat}$ removed from $L1'_{sat}$ has two cases, we use $L1'_{unsat1}$ and $L1'_{unsat2}$ where $L1'_{unsat1}+L1'_{unsat2}=L1'_{unsat}$ to present them.
 In the first case, it might be the same transition (up to renaming) removed from $L2'_{sat}$,
-\[\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L1'_{unsat1}\longrightarrow\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L2'_{unsat}.\]
-
-Or it is the transition not removed in the last iteration because of the inclusion
-\[Assignments_{L2_{sat}, States_{L2_{sat}}}\subseteq Assignments_{L1, States_{L1}}.\] 
-We have already proved that 
-\[Assignments_{L1'_{sat}, States_{L1'_{sat}}}\subseteq Assignments_{L2_{sat}, States_{L2_{sat}}},\]
-so those transitions will be removed this time. In this case,
-\[\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\in L1'_{unsat2}\longrightarrow\ostate{\tilde{t}}\xrightarrow{l}\ostate{\tilde{t'}}\notin L2_{sat}.\]
-
-By induction, if there is no more unsatisfiable transitions in $L2''_{sat}$, so $L2''_{unsat}$ is an empty set and then $L1'_{unsat1}$ is also empty as $L1'_{unsat1}\subseteq L2''_{unsat}$.
+%% \[s\xrightarrow{l}s'\in L1'_{unsat1}\longrightarrow s\xrightarrow{l}s'\in L2'_{unsat}.\]
+
+%% Or it is the transition not removed in the last iteration because of the inclusion
+%% \[Assignments_{L2_{sat}, States_{L2_{sat}}}\subseteq Assignments_{L1, States_{L1}}.\] 
+%% We have already proved that 
+%% \[Assignments_{L1'_{sat}, States_{L1'_{sat}}}\subseteq Assignments_{L2_{sat}, States_{L2_{sat}}},\]
+%% so those transitions will be removed this time. In this case,
+%% \[s\xrightarrow{l}s'\in L1'_{unsat2}\longrightarrow s\xrightarrow{l}s'
+%% \notin L2_{sat}.\]
+
+%% By induction, if there is no more unsatisfiable transitions in $L2''_{sat}$, so $L2''_{unsat}$ is an empty set and then $L1'_{unsat1}$ is also empty as $L1'_{unsat1}\subseteq L2''_{unsat}$.
 The transitions to remove should only belong to $L1'_{unsat2}\nsubseteq L2''_{sat}$.
@@
 It implies that $States_{L1_{reach}}=States_{L2_{reach}}$ and
-$$Assignments_{L1_{reach},States_{L1_{reach}}}=Assignments_{L2_{reach},States_{L2_{reach}}}.$$
+%% $$Assignments_{L1_{reach},States_{L1_{reach}}}=Assignments_{L2_{reach},States_{L2_{reach}}}.$$
 \hfill\qed
@@
 
-\ERIC{Proof sketch:}
-
-  Proof similar to the previous case still apply here, but adapted as
-  we are building a different starting point :
-
-  - Define the function $States$ as before, and  $Assignments : OT^* \# State -> $ the function
-  computing the set of assignments of a global state from a given set of OTs.
-
-  - The structure implicitely computed by the algorithm (comprised in
-  the structure of an Open Automaton) is a triple $ Aut= <States, OTs,
-  Assigns>$.
-
-  - when building $L1$ and $L2$ the 2 algorithms compute the initial
-  $Aut_0$ structures, without using previous assignments, as
-  explained in section~\ref{section:implementation}.
-
-  - The function $Refine : Aut->Aut$, implemented as
-  $makeReachableSubAutomaton(S0,OTs)$, uses the assignments of the
-  previous step to refine the computed reachable space, reducing all 3
-  components of the triple: by pruning some Unsat OTs, it potentialy
-  removes the corresponding assignments, and their target states.
-
-  - the whole computation takes place within a finite domain: Global
-  states are within the cartesian product of the pLTS states; OTs are
-  always subsets of $L1$, and Assignments are a fixed finite set of
-  symbolic assignements of expressions to state variables,
-  syntacticaly contained in the OTs in $L1$; so the fixpoint
-  computation terminates.
-
-  - the result $Aut$ contains all reachable OTs and States from $L1$,
-  and only these (proof should be similar to that of Th2).
+%% \ERIC{Proof sketch:}
+
+%%   Proof similar to the previous case still apply here, but adapted as
+%%   we are building a different starting point :
+
+%%   - Define the function $States$ as before, and  $Assignments : OT^* \# State -> $ the function
+%%   computing the set of assignments of a global state from a given set of OTs.
+
+%%   - The structure implicitely computed by the algorithm (comprised in
+%%   the structure of an Open Automaton) is a triple $ Aut= <States, OTs,
+%%   Assigns>$.
+
+%%   - when building $L1$ and $L2$ the 2 algorithms compute the initial
+%%   $Aut_0$ structures, without using previous assignments, as
+%%   explained in section~\ref{section:implementation}.
+
+%%   - The function $Refine : Aut->Aut$, implemented as
+%%   $makeReachableSubAutomaton(S0,OTs)$, uses the assignments of the
+%%   previous step to refine the computed reachable space, reducing all 3
+%%   components of the triple: by pruning some Unsat OTs, it potentialy
+%%   removes the corresponding assignments, and their target states.
+
+%%   - the whole computation takes place within a finite domain: Global
+%%   states are within the cartesian product of the pLTS states; OTs are
+%%   always subsets of $L1$, and Assignments are a fixed finite set of
+%%   symbolic assignements of expressions to state variables,
+%%   syntacticaly contained in the OTs in $L1$; so the fixpoint
+%%   computation terminates.
+
+%%   - the result $Aut$ contains all reachable OTs and States from $L1$,
+%%   and only these (proof should be similar to that of Th2).
 
@@
                 \\\specialrule{0em}{1pt}{1pt} 
-                ``P<<(Q<<R)'' State-based		&
+              %  ``$P<<(Q<<R)$'' 
+                State-based		&
                 359 ms 				&

### 2019-04-10 2017-Xudong-SMT/ActaInformatica.tex
Refine proof 2&3

@@
 
- Let $pn=$ be a pNet. The set of states 
+ Let $pn$ be a pNet. The set of states 
  managed by the two algorithms both are subsets of the cartesian
- product of the PLTS states, as defined in page \pageref{def-states}. In a
+ product of the pLTS states, as defined in page \pageref{def-states}. In a
  similar way, the set of state variables attached to each state are
@@
   12, there exists an OT
-  $S_n \xrightarrow{l_{n}}S$ in $L1_{sat}$, with $l'_n=Rename(l_n)$;
+  $S_n \xrightarrow{l_{n+1}}S$ in $L1_{sat}$, with $l'_{n+1}=Rename(l_{n+1})$;
   this OT will be checked and found SAT, so
@@
   Conversely, if $|S|_{L1_{reach}}=n+1$, we get a similar chain in
-  $L1_{reach}$, with the transition $S_n \xrightarrow{l_{n}}S$.  Then $ S_n \in
-  States(L1_{reach})$ and $l_n$ is satisfiable. By induction, we have
+  $L1_{reach}$, with the transition $S_n \xrightarrow{l_{n+1}}S$.  Then $ S_n \in
+  States(L1_{reach})$ and $l_{n+1}$ is satisfiable. By induction, we have
   $S_n \in States(L2_{reach})=States(L2_{sat})$, so there exists
-  $l'_n=Rename(L_n)$ that will have
+  $l'_{n+1}=Rename(l_{n+1})$ that will have
   been checked on the fly, in line 6 of Algorithm~\ref{alg3}. Then
-  the transition $S_n \xrightarrow{l'_{n}}S$ will be added to
+  the transition $S_n \xrightarrow{l'_{n+1}}S$ will be added to
   $L2_{sat}$, and thus $S \in States(L2_{reach})$.
@@
 of $Aut^k = Refine(Aut^{k-1})$: either its predicate, checked with the set of
-$Assign(L^{k-1})$, became Unsat; or this OT is at
+$Assign(L^{k-1})$, became UNSAT; or this OT is at
 the end of a sequence starting from a state in $s_0\ \in State(L^k)$,
-the next OT became Unsat, and the following states in the sequence are
+the next OT became UNSAT, and the following states in the sequence are
 not reachable using satisfiable OTs in $Aut^k$. More formaly, there is a chain
 \[s_0\xrightarrow{ot_1}s_1\xrightarrow{ot_2}...s_{n}\xrightarrow{ot_{n+1}}s_{n+1}\]
-with $Pred(ot_1,L^{k-1})$ Unsat, and all states $s_i, i \in [1..n]$
+with $Pred(ot_1,L^{k-1})$ UNSAT, and all states $s_i, i \in [1..n]$
 unreachable in $Aut^k$.
@@
 \medskip
-Now we prove that the triples at the end of the fixpoint computation
+Now we prove that the triples at the end of the fixed point computation
 in both algorithms are equal.
@@
 in algorithm 1 cannot go ``faster'' than in algorithm 3), then prove
-that when the fix-points are reached, then they are the same.
+that when the fixed points are reached, then they are the same.
 
@@
 \item
-  either $Pred(l,L_1^{k-1})$ is Unsat, because of some assignment
+  either $Pred(l,L_1^{k-1})$ is UNSAT, because of some assignment
     $u \in Assigns(L_1^{k-1})$. But $l \in L_2^k$, so its predicate
@@
     $s_0\xrightarrow{l_1}s_1\xrightarrow{l_2}...s_{n}\xrightarrow{l}s_{n+1}$,
-    with $s_0 \in States(L_1^{k-1})$, $Pred(l_1,L_1^{k-1})$ is Unsat, and
+    with $s_0 \in States(L_1^{k-1})$, $Pred(l_1,L_1^{k-1})$ is UNSAT, and
     all further states unreachable in $L_1^{k-1}$. But as in the
@@
 \smallskip
-Now consider the fixpoints of the $Refine$ iterations. From the
+Now consider the fixed points of the $Refine$ iterations. From the
 initial inclusion $L_2^0\ \subseteq L_1^0$, and our invariant, we get
-inclusion of the fixpoints $L_2^*\ \subseteq L_1^*$.
+inclusion of the fixed points $L_2^*\ \subseteq L_1^*$.
 
 Suppose there exists an OT $l$ in $L_1^*$ that is not in $L_2^*$. This
-means that $Pred(l,Assigns(L_1^*))$ is satisfiable, but
-$Pred(l,L_2^*)$ is satisfiable, that is a contradiction; or as in the
+means that $Pred(l,L_1^*)$ is satisfiable, but
+$Pred(l,L_2^*)$ is not satisfiable, that is a contradiction; or as in the
 invariant proof, there is a similar sequence, with an OT $l_1$

### 2019-04-10 2017-Xudong-SMT/ActaInformatica.tex
some minor changes

@@
 	building predicates expressing the synchronisation conditions
-	between the events of the pNet sub-systems. Checking such
+	between the events of pNet sub-systems. Checking such
 	predicates requires symbolic reasoning about first order logics and application-specific data. We use the Z3 SMT engine to check
@@
 
-Parameterised Networks of Synchronised Automata (pNets) were proposed
+Parameterised networks of synchronised automata (pNets) were proposed
 to give a behavioural specification formalism for distributed
@@
 presented, together with a proof of finiteness of the open automaton, under
-reasonable hypotheses on the pNet structure.
+reasonable hypothesis on the pNet structure.
 
@@
 	generated by the algorithm.
-	\item We define a strategy checking satisfiability of open transitions in the course of the residual algorithm, and show that  the reachable part of the open automaton can be generated and it is minimal with respect to the decidability of predicate satisfiability.
+	\item We define a strategy checking satisfiability of open transitions in the course of the residual algorithm, and show the correctness of the optimised algorithm w.r.t. the original one.
+	% the reachable part of the open automaton can be generated and it is minimal with respect to the decidability of predicate satisfiability.
 	\item We show the usage of this approach on various use-cases from different settings, including an
@@
 external automatic theorem 
-provers (ATP) or automatic tactics from interactive theorem
-provers (ITP), to perform symbolic reasoning, and for example to
+provers (ATPs) or automatic tactics from interactive theorem
+provers (ITPs), to perform symbolic reasoning, and for example to
 discharge some subgoals in the proofs.
@@
 architecture from the nanosatellite case-study. 
-Finally we conclude and discuss perspectives in Section
+Finally, we conclude and discuss perspectives in Section
 \ref{section:conclusion}.
@@
 \cite{Milner89} or of usual point-to-point message passing calculi,
-but it also allows 
+but they also allow 
 for more general mechanisms, like gate negotiation in LOTOS~\cite{LotosISO89}, or broadcast
@@
 		\item $\mathit{Constrs}$ is a set of \emph{constructor operators}: for each $\mathit{Con} \in \mathit{Constrs}$, $arity(Con)=n \in \mathbb{N}$ is its arity 
-		and '$Con : (\mathit{sel}_1,\mathit{sort}_1), \dots, (\mathit{sel}_n,\mathit{sort}_n) \rightarrow \mathit{sort}$' is its signature with the associated selectors.
+		and $Con : (\mathit{sel}_1,\mathit{sort}_1), \dots, (\mathit{sel}_n,\mathit{sort}_n) \rightarrow \mathit{sort}$ is its signature with the associated selectors.
 		For each argument, the pair $(\mathit{sel}_i,\mathit{sort}_i)$ defines an auxiliary
@@
 		\item $Ops$ is a set of \emph{auxiliary operators}, with their
-		arity and signature, of the form: $Op : \mathit{sort}_1, \dots,  \mathit{sort}_n \rightarrow
+		signatures in the form: \\ $Op : \mathit{sort}_1, \dots,  \mathit{sort}_n \rightarrow
 		\mathit{sort}$.
@@
 
+In Table~\ref{table:BIPalgebra} we give an algebra presentation.
 Sorts \texttt{Bool} and \texttt{Int} are predefined with standard operators.
@@
 \begin{table}[t]\caption{\label{table:BIPalgebra}\leftline{Algebra
-			Presentation: predefined Sorts and Operators}}
-	\begin{tabular}{p{3cm}p{3cm}p{6cm}}
+			presentation: predefined sorts and operators}}
+	\begin{tabular}{p{2.8cm}p{2.8cm}p{5cm}}
 		\hline\specialrule{0em}{1pt}{1pt}
@@
 		\item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
-		synchronisation vectors ($K\in\I_\P$).  It is required that \linebreak $\forall k\!\in\! K,
-		\symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k\,|\,g_k$, where
-		$\alpha'_k\in \actions{\variables}$, $I_k\subseteq I$, $J_k\subseteq J$, and 
+		synchronisation vectors ($K\in\I_\P$).  It is required that each
+		$\symb{SV}_k$ is a pair $(\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k,\ g_k)$, where
 		$\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
-			J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
+			J_k}{\vars({\alpha_l})}$, $\alpha'_k\in \actions{\variables}$, $I_k\subseteq I$, and $J_k\subseteq J$. The global action of a vector $\symb{SV}_k$ is
 		$\alpha'_k$. The Boolean expression $g_k $, with $\vars(g_k)\subseteq \bigcup_{l\in 
@@
 
-The semantics of open pNets will be defined as an open automaton, that
+The semantics of an open pNet will be defined as an open automaton, which
 is an automaton where each transition represents the composition transitions 
@@
 	\land
-	\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v'
+	\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v' . 
 \end{multline*}
@@
 \EndWhile
-\State $\mathit{L1}$=filterUnsatTransitions($\mathit{L,Assignments}$);
-\State $\mathit{OA_1^0}$=makeReachableSubAutomaton($\mathit{InitState}(P),L1)$;
-\Repeat $\mathit{OA_1^n}$=RefineReachableSubAutomaton($\mathit{OA_1^{n-1}}$)
+\State $\mathit{L1}$=\textit{filterUnsatTransitions}($\mathit{L,Assignments}$);
+\State $\mathit{OA_1^0}$=\textit{makeReachableSubAutomaton}($\mathit{InitState}(P),L1)$;
+\Repeat $\mathit{OA_1^n}$=\textit{RefineReachableSubAutomaton}($\mathit{OA_1^{n-1}}$)
 \Until  $\mathit{OA_1^n}=\mathit{OA_1^{n-1}}$;   \hfill $\setminus \setminus$ Fixed point reached
@@
 the predicate of each OT is translated 
-into SMTlib assertions (see Section~\ref{section:pruning}), and checked for
-satisfiability (function \texttt{filterUnsatTransitions}). 
+into SMTlib assertions (see Section~\ref{section:pruning}), and then checked for
+satisfiability (function \textit{filterUnsatTransitions}). 
 Then we compute (lines 12-14) the set of reachable transitions and states to build
@@
 cartesian product:  
-$\overline{comb} = (\inactive\cup \overline{ot}_1) \times (\inactive\cup \overline{ot}_2)\times \dots \times (\inactive\cup \overline{ot}_n)$.
+$$\overline{comb} = (\inactive\cup \overline{ot}_1) \times (\inactive\cup \overline{ot}_2)\times \dots \times (\inactive\cup \overline{ot}_n). $$
 
@@
 
-Function \texttt{filterUnsatTransitions}, in line 11 of
-Algorithm\ref{alg1}, and function \\
-\texttt{RefineReachableSubAutomaton}
-in line 13, make use of the Z3 engine to implement the
+In Algorithm~\ref{alg1}, functions \textit{filterUnsatTransitions} (in line 11) 
+\textit{RefineReachableSubAutomaton} (in line 13) make use of the Z3 engine to implement the
 satisfiability checking, for all the OTs computed that far.
@@
                 \]
-                we need to build a predicate encoding both the OT predicate, and
+                we need to build a predicate encoding both the OT predicate and
 the information available on the possible assignments of the initial
@@
 where each $Assign$ represents one of the possible (symbolic) value of
-variable the state variable $v$.
+ the state variable $v$.
 
@@
 
-The basic algorithm from the previous section potentially explores some
+The basic algorithm introduced above potentially explores some
 areas of the global state space that will not be reachable after
@@
 save some of these useless computation. More precisely, it will still
-create, and submit to Z3, the OTs at the ``border'' of the state-space, but
+create, and submit to Z3, the OTs at the ``border'' of the state space, but
 not the transitions issued from non-reachable global states. We use
@@
 they cannot be complete before exploring (at least) all the reachable
-state space. We first need to compute a first over-approximation of
+state space. We first need to compute an over-approximation of
 the reachable state space and assignment sets; this corresponds to
@@
 far (line 12), and compute the final reachable sub-automaton
-iteratively (lines 13-15), in the same way than in algorithm \ref{alg1}. 
+iteratively (lines 13-15), in the same way as in Algorithm \ref{alg1}. 
 Naturally, this step is only useful if there are some assignments.
@@
 \medskip
-Now we will prove that the smart algorithm computes the same 
-open automaton.
+Now we will prove that the smart algorithm computes essentially the same 
+open automata as those of the original algorithm.
 
@@
   \label{Th:CorrectnessWithoutAssignments}
-For a pNet verifying the finiteness conditions of theorem 1, and
-containing no assignment to state variables, then the smart  
+For a pNet satisfying the finiteness conditions of Theorem~\ref{Th:finiteness} and
+containing no assignment to state variables, the smart  
 algorithm, without a final reachability computation, computes 
-the same open automaton as that of Algorithm 1 up to a renaming of
+the same open automaton as that of Algorithm~\ref{alg1} up to a renaming of
 variables in the transition labels.  
@@
 
-\begin{proof}[Theorem \ref{Th:CorrectnessWithoutAssignments}]
+\begin{proof} %[Theorem \ref{Th:CorrectnessWithoutAssignments}]
 
@@
     \item $L1_{reach}$: the final set of OTs of Algorithm~\ref{alg1}, as computed
-      by line 12 (as $OA_1^0$). Without assignments the following
-      refinement step will do nothing, the fixpoint is already reached.
+      by line 12 (as $OA_1^0$). 
+      %Without assignments the following
+      %refinement step will do nothing, the fixpoint is already reached.
     \item $L2_{sat}$: the original set of transitions by Algorithm~\ref{alg3}
@@
 
-\centerline{$L1_{reach} \subseteq L1_{sat} \subseteq L0$}
-\centerline{$L2_{reach}\subseteq  L2_{sat}$}
+\centerline{$L1_{reach} \subseteq L1_{sat} \subseteq L0$ \qquad \mbox{and}\qquad
+$L2_{reach}\subseteq  L2_{sat}$\ .}
+%\centerline{$L2_{reach}\subseteq  L2_{sat}$}
 
@@
 Algorithm~\ref{alg1}. Formally, we have that
-$L2_{sat} \subseteq Rename(L0)$ (up to renaming of fresh variables), and as a consequence $States(L2_{reach})\subseteq  States(L0)$, i.e.,\\
-\centerline{$\forall \ostate{\overline{u}}\in States(L2_{reach}), \exists\ostate{\overline{t}}\in States(L0), \ostate{\overline{t}}=\ostate{\overline{u}}$}
+$L2_{sat} \subseteq Rename(L0)$ (up to a renaming of fresh variables), and as a consequence $States(L2_{reach})\subseteq  States(L0)$, i.e.,\\
+\centerline{$\forall \ostate{\overline{u}}\in States(L2_{reach}), \exists\ostate{\overline{t}}\in States(L0), \ostate{\overline{t}}=\ostate{\overline{u}}$\ .}
 
@@
 \medskip
-We will prove by induction on the distance from the original state,
-that $\forall S \in L0. \forall n \in \mathbb{N}. S \in States(L2_{reach}) \land |S|_{L2_{reach}}=n \Rightarrow S
+We will prove by induction on the distance from the original state
+that\linebreak $\forall S \in L0. \forall n \in \mathbb{N}. S \in States(L2_{reach}) \land |S|_{L2_{reach}}=n \Rightarrow S
 \in States(L1_{reach})$, and vice-versa.
@@
 
-Note that $L0$ is finite, so we conclude $L1_{reach}=L2_{reach}$, and
+Note that $L0$ is finite. Therefore, we can conclude that $L1_{reach}=L2_{reach}$ and
 $States(L1_{reach})=States(L2_{reach})$. 
-
-%  If there is an initial state $\ostate{\overline{t_0}}\in States(L2_{reach})$ then the initial state of the original automaton $\ostate{\overline{t_0}}\in States(L1_{reach})$ must exists.
-
-%% \noteInEM{What you are doing below is a proof by recursion on the
-%%   length of the path reaching a given OT, isn't it ? I suggest you
-%%   explicite this and conclude $L2_{reach}\subseteq  L1_{reach}$.}
-
-%% Suppose that  $\ostate{\overline{t}}\in States(L2_{reach})$. It is reachable in the result automaton of Algorithm 3, so there exists a sequence of transitions 
-%% \[\ostate{\overline{t_0}}\xrightarrow{l_1}\ostate{\overline{t_1}}\xrightarrow{l_2}...\xrightarrow{l_{n}}\ostate{\overline{t}}\] where in each label of the transition $Pred_{l_i}^{i\in [1,n]}$ is satisfiable.
-For the same state $\ostate{\overline{t}}\in States(L1_{reach})$, there exists a sequence of transitions \[\ostate{\overline{t_0}}\xrightarrow{l'_1}\ostate{\overline{t_1}}\xrightarrow{l'_2}...\xrightarrow{l'_{n}}\ostate{\overline{t}}\]where for each transition $Rename(\ostate{\overline{t_{i-1}}}\xrightarrow{l_{i}}\ostate{\overline{t_{i}}}) = \ostate{\overline{t_{i-1}}}\xrightarrow{l'_{i}}\ostate{\overline{t_{i}}}$ and $Pred_{l'_i}^{i\in [1,n]}$ is satisfiable.
-%% From the structure of the algorithms, 
-%% \[\forall \ostate{\overline{t}}\in States(L2_{reach}), \ostate{\overline{t}}\xrightarrow{l'_{n+1}}\ostate{\overline{t'}}\in L2_{reach}\]
-%% \[\exists \ostate{\overline{t}}\xrightarrow{l_{n+1}}\ostate{\overline{t'}}\in L1 \quad s.t.\quad Rename(\ostate{\overline{t}}\xrightarrow{l_{n+1}}\ostate{\overline{t'}}) = \ostate{\overline{t}}\xrightarrow{l'_{n+1}}\ostate{\overline{t'}})\]
-%% where $Pred_{l_{n+1}}$ and $Pred_{l'_{n+1}}$ are satisfiable.
-
-%% Then we can get a new longer sequence \[\ostate{\overline{t_0}}\xrightarrow{l_1}\ostate{\overline{t_1}}\xrightarrow{l_2}...\xrightarrow{l_{n}}\ostate{\overline{t}}\xrightarrow{l_{n+1}}\ostate{\overline{t}}\] \[\Rightarrow\ostate{\overline{t'}}\in States(L1_{reach})\wedge\ostate{\overline{t}}\xrightarrow{l_{n+1}}\ostate{\overline{t'}}\in L1_{reach}\in L1.\] So for arbitrary transition in $L2_{reach}$, there is a same transition in $L1_{reach}$ after renaming its label, then we get
-%% $L2_{reach}\subseteq  L1_{reach}$.
-
-%% Conversely,
-%% \[\forall \ostate{\overline{t'}}\notin States(L2_{reach}), \ostate{\overline{t}}\xrightarrow{l'}\ostate{\overline{t'}}\notin L2_{reach},\quad\exists \ostate{\overline{t'}}\in States(L1), \ostate{\overline{t}}\xrightarrow{l}\ostate{\overline{t'}}\in L1\]
-%% where $Pred_{l}$ and $Pred_{l'}$ are not satisfiable.
-As pruning function in Algorithm 1 will remove all the unsatisfiable transitions, then $\ostate{\overline{t}}\xrightarrow{l}\ostate{\overline{t'}}\notin L1_{reach}$.
-
-%As a result, we get that $L1_{reach}=L2_{reach}$, 
-%We will construct a mapping $f$: $State(L1-reach)\rightarrow
-%State(L2-reach)$.
-%\ERIC{I do not understand this, as states are identical. You would
-%  rather need mapping betwen transitions ?}
-%\begin{enumerate}
-%\setlength{\itemindent}{3.5em}
-%	\item[(Surjective)] If $\ostate{\overline{s_0}}=Initial(p)$ then $f(\ostate{\tilde{s}})=\ostate{\tilde{t_0}}=Initial(p)$ must exists, the transitions started from them fulfill that
-%	\[\forall \ostate{\tilde{t_0'}}, \ostate{\tilde{t_0}}\xrightarrow{v_j}\ostate{\tilde{t_0'}}\in L_{Smart},\quad \exists\ostate{\tilde{s'}},\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}\in L.\]
-%	The state $\ostate{\tilde{t'}}\in State(L_{Smart})$ and as $Pred_j$ of $\ostate{\tilde{t}}\xrightarrow{v_j}\ostate{\tilde{t_0'}}$ is satisfiable, then if the $Pred_i$ of $\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}$ is also satisfiable, the state $\ostate{\tilde{s_0'}}$ is reachable in the original open automaton s.t.
-$\ostate{\tilde{s_0'}}\in State(L1)$, we can construct the mapping
-%	\[f(\ostate{\tilde{s_0'}})=\ostate{\tilde{t_0'}}.\]
-%	If the $Pred_i$ of $\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s_0'}}$ is not satisfiable then two transitions are not matched and $\ostate{\tilde{s_0'}}\notin State(L1)$.
-%	
-%	Let $\textit{Explored}$, $\textit{Explored}_{Smart}$ respectively mean the explored states set of original algorithm and smart algorithm.
-%	
-%	Suppose that  $\ostate{\tilde{s}}\in \textit{Explored}$ there is $\ostate{\tilde{t}}\in \textit{Explored}_{Smart}$ where $f(\ostate{\tilde{s}})=\ostate{\tilde{t}}$, there exists a sequence of transitions $\ostate{\tilde{s_0}}...\xrightarrow{v_i}...\ostate{\tilde{s}}$ and $\ostate{\tilde{t_0}}...\xrightarrow{v_j}...\ostate{\tilde{t}}$.
-%	
-%	The transitions $\ostate{\tilde{s}}\xrightarrow{v}\ostate{\tilde{s'}}$ and $\ostate{\tilde{t}}\xrightarrow{v}\ostate{\tilde{t'}}$ have several cases:
-%	\begin{enumerate}
-%		\item[(1)] $\ostate{\tilde{t'}}\in \textit{Explored}_{Smart}$
-%		
-%		We can find that 
-%		 \[\exists\ostate{\tilde{s'}}\in \textit{Explored},\quad \ostate{\tilde{s}}\xrightarrow{v}\ostate{\tilde{s'}}\quad where\quad f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}.\]
-%		\item[(2)] $\ostate{\tilde{t'}}\notin \textit{Explored}_{Smart}$
-%		
-%		There must has 
-%		\[\exists\ostate{\tilde{s'}}\notin \textit{Explored},\quad \ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}.\]
-%		If the $Pred_i$ of $\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$ is satisfiable then there exists a sequence of transitions $\ostate{\tilde{s_0}}...\xrightarrow{v_i}...\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$.
-So the $\ostate{\tilde{s'}}$ is reachable in the original open automaton, we can construct the mapping
-%		\[f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}.\]
-%		If the $Pred_i$ of $\ostate{\tilde{s}}\xrightarrow{v'}\ostate{\tilde{s'}}$ is not satisfiable then two transitions are not matched and $\ostate{\tilde{s'}}\notin State(L1)$.
-%	\end{enumerate}	
-%	Overall, \[\forall \ostate{\tilde{t}}\in State(L_{Smart}),\quad \exists\ostate{\tilde{s}}\in State(L1), f(\ostate{\tilde{s}})=\ostate{\tilde{t}}.\]
-%	\item[(Injective)] If there is a pair of states $\ostate{\tilde{s}} and \ostate{\tilde{t}}$ constructs the mapping $f(\ostate{\tilde{s}})=\ostate{\tilde{t}}$.
-We can know that $\ostate{\tilde{s}}\in \textit{Explored},\ostate{\tilde{t}}\in \textit{Explored}_{Smart}$.
-%	
-%	As when there is $\ostate{\tilde{t'}}\in \textit{Explored}_{Smart}$, the state is must be $\ostate{\tilde{s'}}\in \textit{Explored}$ where $f(\ostate{\tilde{s'}})=\ostate{\tilde{t'}}$.
-%	So it is a one-to-one mapping.
-%\end{enumerate}
-%
-%Then as the function $f$ is both surjective and injective, it is a bijective function. The theorem is proved.
-%
 \hfill\qed
@@
   \label{Th:CorrectnessWithAssignments}
-In the general case, if a pNet (verifying the finiteness conditions of Theorem 1), contains some assignments to state variables, the smart algorithm computes 
-the same open automaton as that of Algorithm 1 up to a renaming of variables in the transition labels.
+In the general case, if a pNet satisfies the finiteness conditions of Theorem~\ref{Th:finiteness} and contains some assignments to state variables, the smart algorithm computes 
+the same open automaton as that of Algorithm~\ref{alg1} up to a renaming of variables in the transition labels.
 \end{theorem}
@@
           states of) a given set of OTs.
-    \item $Assigns : \overline{OT}, Vars\ \rightarrow \overline{Assign}$: similarily,
-      but for assignments concerning one specific state variable.
+    \item $AssignsVar : Vars\times\overline{OT} \rightarrow \overline{Assign}$: the function of computing the set of assignments of a specific state variable in a transition.
   \end{itemize}
@@
 
-We already know that $L2_{sat}\subseteq L1_{sat}$ (up to renaming),
+We already know that $L2_{sat}\subseteq L1_{sat}$ (up to a renaming),
 because every OT that will be checked positively (using assignments) in line 12 of
-algorithm \ref{alg3} will also be tested by algorithm \ref{alg1} (as
+Algorithm \ref{alg3} will also be tested in Algorithm \ref{alg1} (as
 $L2_{sat}\subseteq L0$), and with a larger set of assignments.
 
-Consequently the initial triples of the refinement loop are:
-
+Consequently, the initial triples of the refinement loop are:
 \begin{align*}
@@
 Aut_2^0 = \langle L2_{sat}, States(L2_{sat}), Assigns(L2_{sat})\rangle \\
-\text{with } Aut_2^0 \subseteq Aut_1^0, \text{ component-wise and up to renaming.}
+\text{with } Aut_2^0 \subseteq Aut_1^0, \text{ component-wise and up to a renaming.}
 \end{align*}
@@
 
-Based on this triple structure, we define the function $Refine : Aut
+Based on each triple structure $Aut$, we define the function $Refine : Aut
 \rightarrow Aut$ modelling the function $makeReachableSubAutomaton(S0,OTs)$. It
@@
 may be reduced:
-$States(L^n)\subseteq States(L^{n-1}) \land Assigns(L^n)\subseteq
-Assigns(L^{n-1})$.
-
-%% \[States_{L'}=\{S_0\}\cup \bigcup States(L'),\]
-%% \[Assignments_{L',States_{L'}}=\bigcup\{Assignments(L', State_{i})\}^{State_{i}\in States_{L'}} \]
-%% \[s.t. |States_{L'}|\le|States_{L}|\wedge|Assignments_{L',States_{L'}}|\le|Assignments_{L,States_{L}}|.\]
-
-\smallskip
-In each iteration $k$, consider a transition $l \in L^k$, define
-
+$$States(L^n)\subseteq States(L^{n-1}) \land Assigns(L^n)\subseteq
+Assigns(L^{n-1})\ .$$
+
+In each iteration $k$, consider a transition $l \in L^k$ and define 
 \[Pred(l,L^{k-1}) = Pred_{l}\wedge \bigwedge_{v\in vars(pn)}\{ \bigvee_{Assign\in
-  Assigns(v,L^{k-1})} Assign\}\]
-
-Checking satisfiability of $l$ means checking satifiability of
+  AssignsVar(v,L^{k-1})} Assign\}\ .\]
+Checking the satisfiability of $l$ means checking the satifiability of
 $Pred(l,L^{k-1})$.
-
-%% \noteInEM{Xudong: Previous version looks wrong to me, because the
-%%   disjunction is between the various possible assignments of each
-%%   state var, but then you need the conjunction of the information for
-%%   all considered vars:
-%% \[\bigvee_{Assign_i\in Assignments_{L, States_{L}}}(Pred_{l}\wedge
-%% Assign_{i})\text{ is true}.\]}
-
-Note that this is equivalent to the predicate defined in section
-\ref{section:pruning}, because we consider all states variables of the
+Note that this is equivalent to the predicate defined in Section
+\ref{section:pruning}, because we consider all state variables of the
 pNet, rather than those of state $s$, but assignments
@@
 of $Aut^k = Refine(Aut^{k-1})$: either its predicate, checked with the set of
-$Assign(L^{k-1})$, became UNSAT; or this OT is at
+$Assign(L^{k-1})$, becomes UNSAT; or this OT is at
 the end of a sequence starting from a state in $s_0\ \in State(L^k)$,
-the next OT became UNSAT, and the following states in the sequence are
-not reachable using satisfiable OTs in $Aut^k$. More formaly, there is a chain
+the next OT becomes UNSAT, and the following states in the sequence are
+not reachable using satisfiable OTs in $Aut^k$. More formally, there is a chain
 \[s_0\xrightarrow{ot_1}s_1\xrightarrow{ot_2}...s_{n}\xrightarrow{ot_{n+1}}s_{n+1}\]
-with $Pred(ot_1,L^{k-1})$ UNSAT, and all states $s_i, i \in [1..n]$
+with $Pred(ot_1,L^{k-1})$ being UNSAT, and all states $s_i, i \in [1..n]$, are
 unreachable in $Aut^k$.
@@
 \smallskip
-In each iteration, the number of triples may decrease, thus there
-exists a sequence \[Aut^n = Refine(Aut^{n-1})\quad s.t. |Aut^n| <
+In each iteration, the number of triples decreases, thus there
+exists a sequence \[Aut^n = Refine(Aut^{n-1})\quad s.t. \ |Aut^n| <
 |Aut^{n-1}|.\]
@@
 transition, reaching the fixed point $Aut^n = Refine(Aut^{n-1})$. The
-initial structure is finite by theorem \ref{Th:finiteness}, so the
+initial structure is finite by Theorem \ref{Th:finiteness}, so the
 iteration always terminates.
@@
 We already have $Aut_2^0\ \subseteq Aut_1^0$.
-We will prove in 2 steps:
+We will proceed in two steps:
 first prove by induction that $Hyp^k = (L_2^k\ \subseteq L_1^k)$ is
-preserved by application of $Refine$ (meaning that the refine function
-in algorithm 1 cannot go ``faster'' than in algorithm 3), then prove
-that when the fixed points are reached, then they are the same.
-
-Suppose $Hyp^{k-1}$, and prove $Hyp^k$.
+preserved by each application of $Refine$ (meaning that the refine function
+in Algorithm~\ref{alg1} cannot go ``faster'' than in Algorithm~\ref{alg3}), then prove
+that when the fixed points are reached, they are the same.
+
+Suppose $Hyp^{k-1}$ holds and let us prove the validity of $Hyp^k$.
 Consider an OT $l\ \in L_2^k$, but $l\ \notin L_1^k$.
@@
 Now consider the fixed points of the $Refine$ iterations. From the
-initial inclusion $L_2^0\ \subseteq L_1^0$, and our invariant, we get
-inclusion of the fixed points $L_2^*\ \subseteq L_1^*$.
+initial inclusion $L_2^0\ \subseteq L_1^0$ and our invariant, we get the
+inclusion  $L_2^*\ \subseteq L_1^*$.
 
@@
 means that $Pred(l,L_1^*)$ is satisfiable, but
-$Pred(l,L_2^*)$ is not satisfiable, that is a contradiction; or as in the
-invariant proof, there is a similar sequence, with an OT $l_1$
-bringing the contradiction.
-
-So we conclude $L_2^* = L_1^*$
-
-%% First, there is an inclusion relation between the initial assignments sets, 
-%% \begin{align*}
-%% &L2_{sat}\subseteq L1\Rightarrow States_{L2_{sat}}\subseteq State_{L1}\\
-%% \Rightarrow &Assignments_{L2_{sat}, States_{L2_{sat}}}\subseteq Assignments_{L1, States_{L1}}
-%% \end{align*}
-
-%% Then we come to see what changes have occurred during the iterations.
-In the first iteration, the inclusion relation between their assignments implies an inclusion relation of unsatisfiable transitions.
-If there are two transitions $s\xrightarrow{l}s' \in L1_{unsat}$ and $s\xrightarrow{l}s' \in L2_{unsat},$ then
-%% \begin{align*}
-%% &\bigvee_{Assign_i\in Assignments_{L1, States_{L1}}} (Pred_{l}\wedge Assign_i)\text{ is false}\\
-%% \text{implies }&\bigvee_{Assign_j\in Assignments_{L2_{sat}, States_{L2_{sat}}}} (Pred_{l}\wedge Assign_j)\text{ is false}.
-%% \end{align*}
-%% From the relation $\forall s\xrightarrow{l}s' \in L1_{unsat},\exists s\xrightarrow{l}s' \in L2_{unsat}$, it can be implied that $L1_{unsat}\subseteq L2_{unsat}.$
-
-%% However, its reverse direction is not fulfilled. Recall that $L1_{sat}=L2_{sat}$, more inclusion relations of the assignments can be implied,
-%% \begin{align*}
-%% Assignments_{L1, States_{L1}}&\supseteq Assignments_{L2_{sat}, States_{L2_{sat}}}\\
-%% &\supseteq Assignments_{L1_{sat}-L1_{unsat}, States_{(L1_{sat}-L1_{unsat})}}\\
-%% &\supseteq Assignments_{L2_{sat}-L2_{unsat}, States_{(L2_{sat}-L2_{unsat})}}
-%% \end{align*}
-
-%% Let $L1'_{sat}=L1_{sat}-L1_{unsat}$ and $L2'_{sat}=L2_{sat}-L2_{unsat}$
-%% Then in the next iteration, the unsatisfiable transition $s\xrightarrow{l}s'\in L1'_{unsat}$ removed from $L1'_{sat}$ has two cases, we use $L1'_{unsat1}$ and $L1'_{unsat2}$ where $L1'_{unsat1}+L1'_{unsat2}=L1'_{unsat}$ to present them.
-In the first case, it might be the same transition (up to renaming) removed from $L2'_{sat}$,
-%% \[s\xrightarrow{l}s'\in L1'_{unsat1}\longrightarrow s\xrightarrow{l}s'\in L2'_{unsat}.\]
-
-%% Or it is the transition not removed in the last iteration because of the inclusion
-%% \[Assignments_{L2_{sat}, States_{L2_{sat}}}\subseteq Assignments_{L1, States_{L1}}.\] 
-%% We have already proved that 
-%% \[Assignments_{L1'_{sat}, States_{L1'_{sat}}}\subseteq Assignments_{L2_{sat}, States_{L2_{sat}}},\]
-%% so those transitions will be removed this time. In this case,
-%% \[s\xrightarrow{l}s'\in L1'_{unsat2}\longrightarrow s\xrightarrow{l}s'
-%% \notin L2_{sat}.\]
-
-%% By induction, if there is no more unsatisfiable transitions in $L2''_{sat}$, so $L2''_{unsat}$ is an empty set and then $L1'_{unsat1}$ is also empty as $L1'_{unsat1}\subseteq L2''_{unsat}$.
-The transitions to remove should only belong to $L1'_{unsat2}\nsubseteq L2''_{sat}$.
-So the iteration continues removing all the transitions not in $L2''_{sat}$, until $L1_{reach}=L2_{reach}$.
-It implies that $States_{L1_{reach}}=States_{L2_{reach}}$ and
-%% $$Assignments_{L1_{reach},States_{L1_{reach}}}=Assignments_{L2_{reach},States_{L2_{reach}}}.$$
+$Pred(l,L_2^*)$ is not satisfiable, which is a contradiction; or as in the
+invariant proof, there is a similar sequence with an OT $l_1$ that leads to
+a contradiction.
+
+Therefore, we conclude that $L_2^* = L_1^*$.
 \hfill\qed
@@
 Then we give detailed results for the Failure Controller that was
-presented in \cite{AVOCS18}, and show how this sort of BIP Architectures
+presented in \cite{AVOCS18}, and show how this sort of BIP architectures
 can be composed together.
-Finally we give some figures illustrating the benefits of the smart
+Finally, we give some figures illustrating the benefits of the smart
 algorithm on these examples.

### 2019-04-10 2017-Xudong-SMT/ActaInformatica.tex
more on proof 3

@@
 
-Suppose there exists an OT $l$ in $L_1^*$ that is not in $L_2^*$. This
-means that $Pred(l,L_1^*)$ is satisfiable, but
-$Pred(l,L_2^*)$ is not satisfiable, which is a contradiction; or as in the
-invariant proof, there is a similar sequence with an OT $l_1$ that leads to
-a contradiction.
+Suppose there exists an OT $l$ in $L_1^*$ that is not in $L_2^*$.
+The fact that $l \in L_1^*$ means that $Pred_l$, with the information contained in $Assigns(L_1^*)$, is satisfiable, but also all the transitions $\{l_i\}_{i \in [1..n]}$ in a sequence
+$s_0\xrightarrow{l_1}s_1\xrightarrow{l_2}...s_{n}\xrightarrow{l_{n+1}}s_{n+1}$ leading to this $l_{n+1}=l$.
+
+Clearly all these $\{l_i\}_{i \in [1..n]}$ were also satisfiable and reachable in $L_2^0$ during the ``smart'' traversal, which did not use assignments.
+Now consider the chain of assignment sets $\{Assigns(L_2^i)\}_{i \in [0..k]}$, used during the iteration of $Refine$ by algorithm \ref{alg3}; we argue that the specific instanciation of variables that makes $Pred(l,L_1^*)$ satisfiable was contained in $Assigns(L_2^0)$, and that if it were removed during one of the $Refine$ step in algorithm \ref{alg1}, then it would be remove similarily during algorithm \ref{alg3}.
+So we get a contradiction.
 
@@
 The result (SAT or UNSAT) of the final \texttt{check-sat} command in
-the translation () is then decoded.
+the translation is then decoded.
 
@@
 
+\vspace{-5mm}
 \begin{figure}[ht]
 \centerline{ 
-  \includegraphics[width=0.30\linewidth]{ActaXFIG/Enable1-aut}
+  \includegraphics[width=0.25\linewidth]{ActaXFIG/Enable1-aut}
   \hspace{25mm}
-  \includegraphics[width=0.25\linewidth]{ActaXFIG/Enable2-aut}}
+  \includegraphics[width=0.20\linewidth]{ActaXFIG/Enable2-aut}}
   \begin{minipage}{5.7cm}
@@
 the holes $P$ and $Q$. Their transitions do not rely on a particular
-implementation of the controllers, but only encode the logical
+implementation of the controllers, but only encode the 
 relations between the actions of the holes.
-We have shown in \cite{henrio:Forte2016} how to prove these two automata are bisimilar.
+We have shown in \cite{henrio:Forte2016} how to prove that they are bisimilar.
 
@@
 
-Now let us revisit the Enable composition from
-Figure~\ref{schema:enable-composed}. Its open automaton is shown in
-Figure~\ref{schema:enable3bis}. Building the symmetric system ``$(P>>Q)>>R$'' in a similar
-way will allow us to prove that they are bisimilar (the Enable
-operator is associative), as we have shown in \cite{HMZ:RR-2016}.
-This approach allows us to study the equational properties of
-many operators in classical process algebras or parallel languages, even
-when their semantics depends on data properties.
-
 \begin{figure}[h]
   \begin{minipage}{2cm}
-  \includegraphics[width=\linewidth]{ActaXFIG/PQR-automaton}
+  \includegraphics[width=0.9\linewidth]{ActaXFIG/PQR-automaton}
   \end{minipage}
   \hspace{10mm}
-  \begin{minipage}{7cm}
+  \begin{minipage}{3.5cm}
   \begin{eqnarray*}
@@
                         }
-    {\ostate{10} \xrightarrow{a2} \ostate{10}}\\
+    {\ostate{10} \xrightarrow{a2} \ostate{10}}
+    \end{eqnarray*}
+  \end{minipage}
+  \hspace{10mm}
+  \begin{minipage}{4cm}
+  \begin{eqnarray*}
     OT_4 & = \openrule{
@@
 \end{figure}
+
+Now let us revisit the Enable composition from
+Figure~\ref{schema:enable-composed}. Its open automaton is shown in
+Figure~\ref{schema:enable3bis}. Building the symmetric system ``$(P>>Q)>>R$'' in a similar
+way will allow us to prove that they are bisimilar (the Enable
+operator is associative), as we have shown in \cite{HMZ:RR-2016}.
+This approach allows us to study the equational properties of
+many operators in classical process algebras or parallel languages, even
+when their semantics depends on data properties.
 

### 2019-04-10 2017-Xudong-SMT/ActaInformatica.tex
a few typos corrected

@@
   Min Zhang (\email{mzhang@sei.ecnu.edu.cn}) \at
-  Shanghai Key Laboratory of Trustworthy Computing, ECNU, China%% \\
+  Shanghai Key Laboratory of Trustworthy Computing, East China Normal University, China%% \\
   %% \email{marsxd@gmail.com, zechen@sei.ecnu.edu.cn, yxdeng@sei.ecnu.edu.cn, mzhang@sei.ecnu.edu.cn}
@@
 \]
-where each $Assign$ represents one of the possible (symbolic) value of
+where each $Assign$ represents one of the possible (symbolic) values of
  the state variable $v$.
@@
 \EndWhile
-\State $\mathit{L2}$=filterUnsatTransitions($\mathit{L,Assignments}$);
-\State $\mathit{OA_2^0}$=makeReachableSubAutomaton($\mathit{InitState}(P),L2)$;
-\Repeat $\mathit{OA_2^n}$=RefineReachableSubAutomaton($\mathit{OA_2^{n-1}}$)
+\State $\mathit{L2}$=\textit{filterUnsatTransitions}($\mathit{L,Assignments}$);
+\State $\mathit{OA_2^0}$=\textit{makeReachableSubAutomaton}($\mathit{InitState}(P),L2)$;
+\Repeat $\mathit{OA_2^n}$=\textit{RefineReachableSubAutomaton}($\mathit{OA_2^{n-1}}$)
 \Until  $\mathit{OA_2^n}=\mathit{OA_2^{n-1}}$;
@@
 first prove by induction that $Hyp^k = (L_2^k\ \subseteq L_1^k)$ is
-preserved by each application of $Refine$ (meaning that the refine function
+preserved by each application of \textit{Refine} (meaning that the refine function
 in Algorithm~\ref{alg1} cannot go ``faster'' than in Algorithm~\ref{alg3}), then prove
@@
     with $s_0 \in States(L_1^{k-1})$, $Pred(l_1,L_1^{k-1})$ is UNSAT, and
-    all further states unreachable in $L_1^{k-1}$. But as in the
+    all further states are unreachable in $L_1^{k-1}$. But as in the
     previous case, we would have $l_1$ in $L_2^k$ and not in $L_1^k$,
@@
 Clearly all these $\{l_i\}_{i \in [1..n]}$ were also satisfiable and reachable in $L_2^0$ during the ``smart'' traversal, which did not use assignments.
-Now consider the chain of assignment sets $\{Assigns(L_2^i)\}_{i \in [0..k]}$, used during the iteration of $Refine$ by algorithm \ref{alg3}; we argue that the specific instanciation of variables that makes $Pred(l,L_1^*)$ satisfiable was contained in $Assigns(L_2^0)$, and that if it were removed during one of the $Refine$ step in algorithm \ref{alg1}, then it would be remove similarily during algorithm \ref{alg3}.
+Now consider the chain of assignment sets $\{Assigns(L_2^i)\}_{i \in [0..k]}$, used during the iteration of $Refine$ by Algorithm \ref{alg3}; we argue that the specific instantiation of variables that makes $Pred(l,L_1^*)$ satisfiable was contained in $Assigns(L_2^0)$, and that if it were removed during one of the $Refine$ step in Algorithm \ref{alg1}, then it would be removed similarly in Algorithm \ref{alg3}.
 So we get a contradiction.

### 2019-04-10 2017-Xudong-SMT/ActaInformatica.tex
Small typos
a cosmetic change

@@
 ensures the termination of our semantic construction algorithm.
+Note that this theorem and its proof were part of previous versions of this work, when Algorithm 1 did not include the fixpoint Refinement computation.
+Proof of termination of the fixpoint itself will be discussed as part of the proof of Theorem \ref{Th:CorrectnessWithAssignments}.
+
 \begin{theorem}[Finiteness]
@@
 \begin{algorithm}[h]
-\caption{MakeTransitions() \em{for a pNet node}}
+\caption{\emph{MakeTransitions}() for a pNet node}
   \label{alg2}
@@
 
-Clearly all these $\{l_i\}_{i \in [1..n]}$ were also satisfiable and reachable in $L_2^0$ during the ``smart'' traversal, which did not use assignments.
-Now consider the chain of assignment sets $\{Assigns(L_2^i)\}_{i \in [0..k]}$, used during the iteration of $Refine$ by Algorithm \ref{alg3}; we argue that the specific instantiation of variables that makes $Pred(l,L_1^*)$ satisfiable was contained in $Assigns(L_2^0)$, and that if it were removed during one of the $Refine$ step in Algorithm \ref{alg1}, then it would be removed similarly in Algorithm \ref{alg3}.
+Clearly all these $\{l_i\}_{i \in [1..n]}$ are also satisfiable and reachable in $L_2^0$ during the ``smart'' traversal, which does not use assignments.
+Now consider the chain of assignment sets $\{Assigns(L_2^i)\}_{i \in [0..k]}$, used during the iteration of $Refine$ by Algorithm \ref{alg3}; we argue that the specific instantiation of variables that makes $Pred(l,L_1^*)$ satisfiable is contained in $Assigns(L_2^0)$, and that if it is removed during one of the $Refine$ step in Algorithm \ref{alg1}, then it is removed similarly in Algorithm \ref{alg3}.
 So we get a contradiction.
@@
     \centerline{\includegraphics[width=0.8\linewidth]{ActaXFIG/rise4fun1}}
-  \caption{Checking one Open Transition in Z3}  \label{schema:smt-lib}
+  \caption{Checking one open transition in Z3}  \label{schema:smt-lib}
 \end{figure}
@@
   \end{minipage}
-  \caption{Open Automaton for the term ``$P>>(Q>>R)$''}
+  \caption{Open automaton for the term ``$P>>(Q>>R)$''}
   \label{schema:enable3bis}
@@
   \centerline{\includegraphics[width=12cm]{ActaXFIG/FailureTimerOA-v2-2}}
-  \caption{Open Automaton for the Failure Monitor architecture}
+  \caption{Open automaton for the Failure Monitor architecture}
   \label{schema:resultOA1}
@@
 
+\medskip
 	\begin{tabular}{p{4cm}p{3cm}p{3cm}}
@@
   product of the states of the pNet $PLTS_i^{i\in I}$, which is finite by
-  hypothesis. So the top-level residual loop of Algorithm 1 terminates provided each 
+  hypothesis. So the top-level residual loop of Algorithm~\ref{alg1} terminates provided each 
   iteration terminates. The enumeration of open-transitions in line 5 of Algorithm~\ref{alg1} is bounded by the
@@
   of transitions of each PLTS is finite, rule Tr1 is 
-  applied a finite number of times. Therefore, each internal loop of Algorithm~1 terminates, and we obtain finitely many deduction trees and
+  applied a finite number of times. Therefore, each internal loop of Algorithm~\ref{alg1} terminates, and we obtain finitely many deduction trees and
   open transitions.

### 2019-04-11 2016-Weak-FH-Bisim/WeakBisim.tex
clarify substraction
def 11 updated

@@
 
-$\uplus$ is the disjoint operator on sets. We extend it to  disjoint union  of indexed 
+$\uplus$ is the disjoint union on sets. We extend it to  disjoint union  of indexed 
 sets defined by the merge of the 
@@
 %methods of different interfaces).
-$\setminus$ is the standard subtraction operation on sets.
+$\setminus$ is the standard subtraction operation on indexed sets: $\dom(A\setminus B)=\dom(A)\setminus B$.
 
@@
          {s \OTarrow {\alpha} s'}
-         \in \mathcal{T} \] If there is a $j$ such that $A(j)=\tau$ then we have \[ \alpha=\tau\land s=s'\land \Pred=\True\land\Post=\Id(s)
+         \in \mathcal{T} \] If there is a $j$ such that $A(j)=\tau$ then we have \[ \alpha=\tau\land s=s'\land \Pred=\True\land\Post=\Id(s) \land A=(j\mapsto \tau)
 \]
@@
 The second statement ensures that there cannot be in the open automaton other transitions that would be able to observe a silent action from a hole.
+The condition $A=(j\mapsto \tau)$ is a bit restrictive, it could safely be replaced by $\forall h\in\dom(A).\, A(h)=\tau$, allowing the other holes to perform silent transitions too (because these silent actions cannot be observed).
 

### 2019-04-16 2018-Arch-pNets/Coordination Camera ready/arch-pNets.tex
Coordination final: including TODO.txt

--- 2019-02-26 2018-Arch-pNets/arch-pNets.tex
@@
 \cite{CM:FMCO08,HKM-FASE16}. 
-The structure of pNets is static but unbounded.  This allows for model-checking
-approaches even for reconfigurable applications.
+There is no bound on the number of elements inside a pNets or the valuation of parameters.
+When restricted to finite instantiations, it becomes possible to us pNets  for finite model-checking approaches.
 Closed pNets were used to encode fully defined programs or systems,
@@
 ambiguous, we shall use notations for sets, and typically write
-``indexed set over I'', even though formally we should speak of multisets; and
+``indexed set over I'', even though formally we should speak of maps; and
 write $x\in a_i^{i\in I}$ to mean $\exists i\in I.\, x=a_i$.  An empty
@@
 $\actions{\variables}$, with $\actions{\variables}\subseteq\Talg$.
-We define $\assigns{\variables}$ as the set of variable assignments of the form: $(x_i := e_i)^{i \in I}$. 
+We define $\assigns{\variables}$ as the set of variable assignments of the form: $(x_i := e_i)^{i \in I}$ and let 
 %\[
@@
 %to denote the set of \emph{variable assignments}. 
- $u$ ranges over sets of assignments.
+ $u$ range over sets of assignments.
 %To be able to reason about the data flow between actions, we
@@
 %\label{section:pNets}
-A pLTS is a labelled transition system with variables that can be
-used to characterise a state, as part of actions, guards, and
+A pLTS is a labelled transition system with variables occurring inside states,  actions, guards, and
 assignments. 
@@
 Variables of each state are pairwise disjoint.
-We need to introduce input variables to reason about the data flow between actions.
+The parameters of actions that appear on pLTS transitions are either input variables, bound when the action occurs, or expressions using the value of other (i.e. output) variables.
 We  define the set of parameterised actions a pLTS can use ($a$
@@
 
-The red dotted rule expresses an implication but at a different logical level compared to  a normal 
-inference rule. 
+The red dotted rule expresses an implication, stating that if actions of the holes perform the designed actions and the condition is verified, then the variables are modified and the state changes.
+This implication however occurs in a restricted logic with predefined syntax, at a different logical level compared to  a classical
+inference rule expressed in the logic of a scientific paper. 
  The open transition is  a logical implication that uses a simple logic with the 
  expressive power  given by the predicate algebra (it must include logical 
- propositions and equality). We differentiate classical (black) inference rules that use 
- an expressive (higher order) logic and are paper rules from open transition rules that use a simpler  logic,  define automata transitions, and could  be handled 
- mechanically.
+ propositions and equality). 
+ Proposition and inference rules of the paper use a general expressive, while predicates inside the open transitions should use a more restricted logic, typically a logic that could  be handled mechanically and expressed by terms that can be encoded in a simple syntax.
 
@@
     \{t' := t+1\} }
-  {\ostate{11} \OTarrow{\alpha(t)} \ostate{12}}\vspace{-1.3ex}
+  {\ostate{11} \OTarrow{\alpha(t)} \ostate{14}}\vspace{-1.3ex}
   \]
@@
 It requires the hole at label $B$ to fire a $fail(b)$ action, with the condition $b=true$ and the state variable $t<Max$.
-In this case, the global pNet goes from state $\ostate{11}$ to state $\ostate{12}$ where $t'=t+1$.
+In this case, the global pNet goes from state $\ostate{11}$ that has an internal variable $t$ to state $\ostate{14}$ where the state variable $t'$ has the value $t+1$.
 This emits a global action $\alpha(t)$.

### 2019-04-17 2018-Arch-pNets/Coordination Camera ready/arch-pNets.tex
2 proprietes ajoutees en page 15

@@
 
-\paragraph{Practical experiments.}%\noteSB{J'ai repris ce paragraphe}
-%\noteLH{j ai nomme ce paragraphe}
+\paragraph{Practical experiments.}
 The above encoding provides a mechanism for the symbolic verification
@@
 possible firing of some interactions (e.g. OT 2 and 3 for
-{\PortFail}). It looks like the rough behaviour is
-reasonable, although a detailed study shows that the property stated
+{\PortFail}).
+
+\add{Model-checking of open-automaton is out of the scope of this paper,
+though the resulting automaton here is small enough to observe the
+kind of properties we can prove. It is clear that our encoding allows
+to test specific values of state-variables in formulas, like e.g.:
+  \begin{equation}
+    \label{eq:prop:z:top}
+    \AW[\quad]{(z = \topinterval)}{\PortFail} \land\quad
+    \AG \bigl(
+    \PortReset \rightarrow \AW[]{(z = \topinterval)}{\PortFail}
+    \bigr).
+  \end{equation}
+that says that \emph{as long as no failure has occured, the $z$ variable of the
+$\NameTimer$ component has the value $\topinterval$}.
+
+But we can also (as long as we get a proper axiomatisation of our data
+operators in the SMT engine) handle more involved data properties,
+like here the fact that \emph{a reset can only be requested within the
+specified delay after a failure:}
+  \begin{multline}
+    \label{eq:prop:to:delay}
+    \forall T_0, T_1 \in \sZ,\
+    \AG \Big((\PortFail \land \NameTimer.t = T_0) \rightarrow
+    \\
+    \AW[]{\bigl((\PortAsk \land \NameTimer.t = T_1) \rightarrow
+      (T_1 - T_0 \in \NameCtrl.\mathit{zone})\bigr)
+    }{
+      (\PortReset \lor \PortResume)
+    }\Big),
+  \end{multline}
+}
+
+Last, a detailed study shows that the safety property stated
 in page~\pageref{property:reset} does not hold, because of the
@@
 
+\noteEMin{on peut encore bouger deux lignes de l'annexe D.2, pour
+  mentionner ici une propriete de liveness, mais ca va dependre de la
+  place, c'est deja un peu long ici...}
 %% %****************************************************************

### 2019-04-18 2018-Arch-pNets/Coordination Camera ready/arch-pNets.tex
newcoord macro et quelques explications

--- 2019-04-16 2018-Arch-pNets/Coordination Camera ready/arch-pNets.tex
@@
 \newcommand{\replaceSB}[2]{\replace[Replaced by Simon]{#1}{#2}}
+
+\newcommand{\newCoord}[1]{{\color{blue}#1}}
 
@@
 Variables of each state are pairwise disjoint.
-The parameters of actions that appear on pLTS transitions are either input variables, bound when the action occurs, or expressions using the value of other (i.e. output) variables.
+\newCoord{The parameters of actions that appear on pLTS transitions are either input variables, bound when the action occurs and accepting any value (of the right type), or expressions using the value of other variables.}
 We  define the set of parameterised actions a pLTS can use ($a$
@@
 A  pNet  exposes
- global actions resulting from the synchronisation of internal actions in some sub-pNets. 
-This synchronisation  is specified by  \emph{synchronisation vectors}.
+ global actions resulting from the synchronisation of internal actions in some sub-pNets, and some actions of the holes.
+\newCoord{As holes are process parameters, synchronisation with a hole has an obvious concrete meaning when a process is put inside the hole and emits the action.
+We  also define a semantics for open pNets with holes where open transitions express the fact that a pNet can performs a transition provided one or several holes emit some actions.}
+\newCoord{This synchronisation  is specified by  \emph{synchronisation vectors} expressing the synchronous interaction between actions inside sub-pNets and holes, data transmission is expressed classically using action parameters.}
 Actions involved in the synchronisation vectors do
@@
 
-The red dotted rule expresses an implication, stating that if actions of the holes perform the designed actions and the condition is verified, then the variables are modified and the state changes.
+\newCoord{The red dotted rule expresses an implication, stating that if actions of the holes perform the designed actions and the condition is verified, then the variables are modified and the state changes.
 This implication however occurs in a restricted logic with predefined syntax, at a different logical level compared to  a classical
@@
  propositions and equality). 
- Proposition and inference rules of the paper use a general expressive, while predicates inside the open transitions should use a more restricted logic, typically a logic that could  be handled mechanically and expressed by terms that can be encoded in a simple syntax.
+ Proposition and inference rules of the paper use a general expressive, while predicates inside the open transitions should use a more restricted logic, typically a logic that could  be handled mechanically and expressed by terms that can be encoded in a simple syntax.}
 
@@
 This emits a global action $\alpha(t)$.
+\newCoord{Figure~\ref{fig:ArchFailure:OA} illustrates a whole open automaton.}
 %

### 2019-04-18 2018-Arch-pNets/Coordination Camera ready/arch-pNets.tex
intro + data +open transitions

@@
 application of architectures is compositional \wrt safety properties,
-\ie if two architectures guarantee two properties, their composition ensures the conjunction of the properties.
+\ie if two architectures guarantee two properties, their composition ensures the conjunction of the properties \newCoord{but~\cite{AttieBBJS16-architectures-faoc} did not consider properties depending on data}.
 %
@@
 %\paragraph{Contributions}
-The main contributions of this paper are: 1) The definition of a
-theory of BIP architectures with data, including a theorem about
-preservation of (data dependent) properties by 
-compositions. 2) An encoding of architectures with data into  open pNets, allowing for analysis of their temporal properties using pNet's
+The main contributions of this paper are: 1) \newCoord{The addition of data to the
+theory of BIP architectures, including a theorem about
+preservation of data dependent properties by 
+compositions.} 2) An encoding of architectures with data into  open pNets, allowing for analysis of their temporal properties using pNet's
 software tools.  
@@
 
-\newCoord{The red dotted rule expresses an implication, stating that if actions of the holes perform the designed actions and the condition is verified, then the variables are modified and the state changes.
-This implication however occurs in a restricted logic with predefined syntax, at a different logical level compared to  a classical
-inference rule expressed in the logic of a scientific paper. 
- The open transition is  a logical implication that uses a simple logic with the 
+\newCoord{The red dotted rule somehow expresses an implication, stating that if actions of the holes perform the designed actions and the condition is verified, then the variables are modified and the state changes.
+This implication however  uses a simple logic with the
  expressive power  given by the predicate algebra (it must include logical 
  propositions and equality). 
- Proposition and inference rules of the paper use a general expressive, while predicates inside the open transitions should use a more restricted logic, typically a logic that could  be handled mechanically and expressed by terms that can be encoded in a simple syntax.}
+ Proposition and inference rules of the paper use a standard logic, while predicates inside the open transitions should use a more restricted logic, typically a logic that could  be handled mechanically and expressed by terms that can be encoded in a simple syntax.
+Open transitions express in a symbolic way, transitions  that are not only parametrised with variables but also actions of not yet known processes.}
 

### 2019-04-18 2016-Weak-FH-Bisim/WeakBisim.tex
Definition 11 improved

--- 2019-04-09 2016-Weak-FH-Bisim/WeakBisim.tex
@@
          {
-           A,\Pred,\Post}
+           \beta_j^{j\in J},\Pred,\Post}
          {s \OTarrow {\alpha} s'}
-         \in \mathcal{T} \] If there is a $j$ such that $A(j)=\tau$ then we have \[ \alpha=\tau\land s=s'\land \Pred=\True\land\Post=\Id(s)
+         \in \mathcal{T} \] If there is a $j$ such that $\beta_j=\tau$ then we have \[ \alpha=\tau\land s=s'\land \Pred=\True\land\Post=\Id(s) \land J=\{j\})
 \]
@@
 The second statement ensures that there cannot be in the open automaton other transitions that would be able to observe a silent action from a hole.
+The condition $J=\{j\}$ is a bit restrictive, it could safely be replaced by $\forall j\in J.\, \beta_j=\tau$, allowing the other holes to perform silent transitions too (because these silent actions cannot be observed).
 

### 2019-04-23 2016-Weak-FH-Bisim/WeakBisim.tex
update todos
preuve en cours; mardi matin

@@
 
+TODOS: AVRIL 2019
+
+- exemple (Eric: failure buffer)
+- biblio (rabea)
+- inuitions de preuves et intuition de bisim de cloture, etc. (Ludo)
+
+===> dealine 14 Juillet
+
 TODOs du 19 decembre
@@
 
-- on remet l exemple de enable, etendu pour weak (Eric)
-
-- reste nos 5 thm a prouver: transitivite, decomposition/ recomposition, congruence x 2
-
 - etat de l art: il faudrait des refs sur bisim en gemneral, probablement avec pas mal de pi calcul (Eric?), des refs sur pourquoi pnets et des refs sur utilite de la weak bisim en verif
 
-- target SIAvocs ou SCP ou JLamp
+- target: JLamp
 
@@
 \begin{lemma}[Open transition composition]\label{lem-compose}
-	Suppose $j_0\in J$ and:\\[-2ex]
-\begin{mathpar}
-%\[
-P\models{\openrule
-	{
-		\beta_j^{j\in J}, 
-		\Pred,  
-		\Post}
-	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
-		\ostate{s_i'^{\, i\in L}}}
-}%\]
-\text{~~and~~}
-%\[
-Q\models{\openrule
-	{
-		\beta_j^{j\in J_Q},
-		 \Pred\,',  
-		\Post\,'}
-	{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
-		\ostate{s_i'^{\, i\in L_Q}}}
-}%\]
-\end{mathpar}
-Then, we have\\[-2ex]
-	\[ P[Q]_{j_0}  
-	\models
-	{\openrule
-		{
-			\beta_j^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
-			\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0},  
-			\Post\uplus \Post\,'}
-		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {\alpha}
-			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
-	}
-	\]
+
 \end{lemma}
@@
 By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
-$\forall p\!\in\![0..m_1].\openrule
+$\forall p\!\in\![0..m_1].P\models\openrule
     {\set{\beta^1_p},\Pred^1_p,\Post^1_p   }
-         {\ostate{{(s^1_{pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s^1_{(p+1)i})}^{i\in L}}}\!\in\!\mathcal{T} \wedge
-\openrule
+         {\ostate{{(s^1_{pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s^1_{(p+1)i})}^{i\in L}}} \wedge
+P\models\openrule
          {\set{\beta^2},\Pred^2,\Post^2 }
-         {\ostate{({s_{0i}^2})^{i\in L}} \OTarrow {\alpha} \ostate{({s_{1i}^2})^{i\in L}}}\! \in\! \mathcal{T}
+         {\ostate{({s_{0i}^2})^{i\in L}} \OTarrow {\alpha} \ostate{({s_{1i}^2})^{i\in L}}}
 \wedge\\
-\forall p \in [0..m_2].\openrule
+\forall p \in [0..m_2].P\models\openrule
          {
            \set{\beta^3_p},\Pred^3_p, \Post^3_p}
-         { \ostate{(s^3_{pi})^{i\in L}} \OTarrow {\tau} \ostate{(s^3_{(p+1)i})^{i\in L}}} \in \mathcal{T}$ 
+         { \ostate{(s^3_{pi})^{i\in L}} \OTarrow {\tau} \ostate{(s^3_{(p+1)i})^{i\in L}}}$ 
 \\
@@
 \end{mathpar}
-In the same way,  by Lemma \ref{lem-rel-OT-WOT} we can decompose $\WOT_p$ into  a series of $m'+n'$ tau open transitions and a single observable open transition:
-\[Q\models{\openrule
-			{
-				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred'^{2}}},  
-				{{\Post'^{2}}}}
-				{\ostate{s_{i}^{i\in L_Q}} \OTarrow {\alpha_p}
-				\ostate{s_{i}'^{i\in L_Q}}}
-				}%\]
-\]
-
-We proceed by iteration on the list of   $\symb{OT}_p$ of $P$ identified above with an additional variable $t$, OTs are of the form: 
+%In the same way,  by Lemma \ref{lem-rel-OT-WOT} we can decompose $\WOT_p$ into  a series of $m'+n'$ tau open transitions and a single observable open transition:
+%\[Q\models{\openrule
+%			{
+%				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred'^{2}}},  
+%				{{\Post'^{2}}}}
+%				{\ostate{s_{p i}^{i\in L_Q}} \OTarrow {\alpha_p}
+%				\ostate{s_{(p+1) i}^{i\in L_Q}}}
+%				}%\]
+%\]
+
+We proceed by iteration on the list of  OTs of $P$ identified above, these OTs are of the form:
+
 $P\!\models		
@@
          {\ostate{s^{i\in L}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L}_{(p+1)i}}}$
-At the beginning $Q$ is at state $\ostate{s_{0}}$ and $t=0$. 
-For each step, we have two cases:
+
+We use an additional variable $t$, in the iteration, it will be used as an index from $0$ to $n$, i.e. inside the OTs of $Q$.
+At the beginning $t=0$, i.e. $Q$ is at state $\ostate{s_{0}}$. \TODO{on peut remplacer $s_t$ par $s_{t i}^{i\in L_Q}$}
+For each step of the iteration, we have two cases:
 \begin{itemize}
-\item If $j_0\in J$ then Q moves by one open transition. By the hypothesis above $\beta^i_{j_0}\neq \tau$. Additionally, we have
+\item If $j_0\in J$ then Q moves by one open transition. By the hypothesis above $\beta^i_{p j_0}\neq \tau$. Additionally, we have 
 $\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{p=0}^{m_1} \vis{\set{\beta^1_p}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{p=0}^{m_2} \vis{\set{\beta^3_p}}}$ and\\
  $\gamma_{j_0}=[\beta_0..\beta_n]$, thus
-  $\beta^i_{j_0}=\beta_t$ with  for some $t$ such that $t$ has value $0$ at beginning and that is incremented whenever this condition is satisfied.
-
-On the other hand, by hypothesis we have:
+  $\beta^i_{p j_0}=\beta_t$ with  for some $t$ such that $t$ has value $0$ at beginning and that is incremented whenever this condition is satisfied.
+
+On the other hand, by hypothesis we have \TODO{on peut remplacer $s_t$ par $s_{t i}^{i\in L_Q}$}:
 \[Q\models{\openrule
@@
 \]
-By  Lemma \ref{lem-rel-OT-WOT} we can decompose $\WOT_t$ into  a series of $k+k'$ tau open transitions and the observable open transition:
+By  Lemma \ref{lem-rel-OT-WOT} we can decompose this $\WOT$ into  a series of $k+1$ and $k'+1$ tau open transitions and an observable open transition:
+
+\[\forall h\!\in\![0..k].Q\models\openrule
+    {\set{\beta^1_h},\Pred^1_h,\Post^1_h   }
+         {\ostate{{(s^1_{h})}} \OTarrow {\tau} \ostate{{(s^1_{(h+1)})}}}
+\]
 
@@
 	{
-		\gamma_{t j}^{j\in J_t},
-		 \Pred_t,  
-		\Post_t}
-	{\ostate{s^2_{t}}\OTarrow {\alpha_t}
-		\ostate{s^3_{t}}}
+		\set{\beta^2},
+		 \Pred^2,  
+		\Post^2}
+	{\ostate{s^2_{0}}\OTarrow {\alpha_t}
+		\ostate{s^2_{1}}}
 }
 \]
+
+\[
+\forall h \in [0..k'].Q\models\openrule
+         {
+           \set{\beta^3_h},\Pred^3_h, \Post^3_h}
+         { \ostate{(s^3_h)} \OTarrow {\tau} \ostate{(s^3_{(h+1)})}} \]
+
+such that 
+$s_t=s^1_{0} \wedge s^1_{(k+1) i}=s^2_{0} \wedge  s^2_{1}= s^3_{0} \wedge s^3_{(k'+1) i}=s_{t+1}$\\
+
+$\displaystyle{\gamma_{t j}^{j\in J_t}=\mybigdotcup_{h=0}^{k} \vis{\set{\beta^1_h}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{h=0}^{k'} \vis{\set{\beta^3_h}}}\\
+\Pred_t=\bigwedge_{h=0}^{k}\!\big(\Pred^1_h\bigotimes_{j=0}^{h-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{h=0}^{k}\subst{\Post_h^1}\land \bigwedge_{h=0}^{k'}\!\Pred_h^3\big(\bigotimes_{j=0}^{h-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{h=0}^{k}\subst{\Post_h^1}\big)\\
+\Post=\bigotimes_{h=0}^{k'}\Post^3_h\subst{\Post^2}\bigotimes_{j=0}^{k}\subst{\Post^1_j}
+$
+
 \begin{enumerate}
 
-\item For the first $k$ open tau transitions, by Definition \ref{def:Non-ObsTau} $P$ can make a tau open transition and the hole makes also tau action.
-So by Lemma \ref{lem-compose} we obtain $k$ open transitions in the form:
+\item For the first $k$ open tau transitions, by Definition \ref{def:Non-ObsTau} $P$ can necessarily make a tau open transition if the hole indexed $j_0$ makes a tau action.
+So by Lemma \ref{lem-compose} we obtain $k$ open transitions in the form: \TODO{remarquer la notation compliquee ou trouver une meilleure notation mais pas trop lourde}
 \[P[Q]_{j_0}\!\models		
@@
     {
-       \beta_p^{(p\in J\setminus\{j_0\}) \uplus J_Q},{\Pred_p},{\Post_p}   }
-         {\ostate{s^{i\in L \uplus L_Q}_{pi}} \OTarrow {\tau} \ostate{s^{i\in L\uplus L_Q }_{(p+1)i}}}\]
-
-\item We proceed in the same way for $k'$ last weak open transitions, and we obtain $k'$ open tau transitions.\\
-\item For the observable open transition.
-Because of the definition of $\Pred'$ we can suppose that $\alpha_t=\beta_{j_0}$ \TODO{because else the original WOT does not trigger}.
-By Lemma \ref{lem-compose} we obtain:\\
-\[P[Q]_{j_0}\!\models		
-\openrule
-    {
-       \beta_p^{(p\in J\setminus\{j_0\}) \uplus J_Q},{\Pred_p}\!\!'',{\Post_p}\!\!''   }
-         {\ostate{s^{i\in L \uplus L_Q}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L\uplus L_Q }_{(p+1)i}}}\] \\
- such that  ${\Pred_p}\!\!'' \iff {\Pred_p}
-		\land {\Pred_p}\!\!'\land \alpha_t=\beta_{j_0}$, ${\Post_p}\!\!''={\Post_p}\uplus 
-		{\Post_p}\!\!'$\\ 
+       \set{\beta^1_h},{\Pred^1_h},{\Post^1_h}   }
+         {\ostate{s^1_h\uplus s^{i\in L}_{pi} } \OTarrow {\tau} \ostate{s^1_{h+1}\uplus s^{i\in L}_{pi}}}\]
+
+\item For the observable open transition.  By Lemma \ref{lem-compose} we obtain:\\ 
+	\[ P[Q]_{j_0}  
+	\models
+	{\openrule
+		{
+			{\beta^i_{p j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}, 
+			\Pred_p\land\Pred^2\land \alpha_t=\beta^i_{p j_0 },  
+			\Post_p\uplus \Post^2}
+{\ostate{s^{i\in L}_{pi}\uplus s_0^2} \OTarrow {\alpha_p} \ostate{s^{i\in L}_{(p+1)i}\uplus s_1^2}}
+	}
+	\]
+
+%
+%\[P[Q]_{j_0}\!\models		
+%\openrule
+%    {
+%       {\beta^i_{p j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2},{\Pred_p}\!\!'',{\Post_p}\!\!''   }
+%         {\ostate{s^{i\in L \uplus L_Q}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L\uplus L_Q }_{(p+1)i}}}\] \\
+% such that  ${\Pred_p}\!\!'' \iff {\Pred_p}
+%		\land {\Pred_p}\!\!'\land \alpha_t=\beta_{j_0}$, ${\Post_p}\!\!''={\Post_p}\uplus 
+%		{\Post_p}\!\!'$\\ 
+\item We proceed in the same way as the first item for $k'$ last weak open transitions, and we obtain $k'$ open tau transitions.\\
 \end{enumerate}

### 2019-04-24 2016-Weak-FH-Bisim/WeakBisim.tex
work on proof of new lemma 7

@@
 - inuitions de preuves et intuition de bisim de cloture, etc. (Ludo)
+
+\TODO{voisr si on redefinit les bigotimes pour prendre des maps et retourner des maps au lieu des substitutions (et on englobe dans une subst a la fin)}
 
@@
 \begin{lemma}[Open transition composition]\label{lem-compose} 
-
+	Suppose $j_0\in J$ and:\\[-2ex]
+\begin{mathpar}
+%\[
+P\models{\openrule
+	{
+		\beta_j^{j\in J}, 
+		\Pred,  
+		\Post}
+	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
+		\ostate{s_i'^{\, i\in L}}}
+}%\]
+\text{~~and~~}
+%\[
+Q\models{\openrule
+	{
+		\beta_j^{j\in J_Q},
+		 \Pred\,',  
+		\Post\,'}
+	{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
+		\ostate{s_i'^{\, i\in L_Q}}}
+}%\]
+\end{mathpar}
+Then, we have\\[-2ex]
+	\[ P[Q]_{j_0}  
+	\models
+	{\openrule
+		{
+			\beta_j^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
+			\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0},  
+			\Post\uplus \Post\,'}
+		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {\alpha}
+			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
+	}
+	\]
 \end{lemma}
@@
 \end{small}
+
+Note that we also have the following lemma (trivial):
+
+\begin{lemma}[Open transition composition]\label{lem-compose-2} ~\\	Suppose $j_0\not\in J$ and $L_Q=\Leaves({Q})$:\\[-2ex]
+\begin{mathpar}
+%\[
+P\models{\openrule
+	{
+		\beta_j^{j\in J}, 
+		\Pred,  
+		\Post}
+	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
+		\ostate{s_i'^{\, i\in L}}}
+}%\]
+\end{mathpar}
+Then, we have\\[-2ex]
+	\[ P[Q]_{j_0}  
+	\models
+	{\openrule
+		{
+			\beta_j^{j\in J}, 
+			\Pred,  
+			\Post}
+		{\ostate{s_i^{i\in L}\uplus s_i^{i\in L_Q}} \OTarrow {\alpha}
+			\ostate{s_i'^{\, i\in L}\uplus s_i^{i\in L_Q}}}}
+	\]
+\end{lemma}
 
@@
 \begin{lemma}[Weak open transition composition]\label{lem-Weakcompose} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
-	Suppose $j_0\in J$ and $\gamma_{j_0}=[\beta_0..\beta_n]$ and additionally:\\[-2ex]
+	Suppose $j_0\in J$  and additionally:\\[-2ex]
 \begin{mathpar}
@@
 	{
-		\gamma_j^{j\in J}, 
+		\beta_j^{j\in J}, 
 		\Pred,  
 		\Post}
-	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
+	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
 		\ostate{s_i'^{\, i\in L}}}
 }\\
-\text{~~and for all $p\in[0..n]$~~}
+\text{~~and~~}
 Q\models{\openrule
 	{
-		\gamma_{p j}^{j\in J_p},
-		 \Pred_p,  
-		\Post_p}
-	{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
-		\ostate{s_{(p+1) i}^{\, i\in L_Q}}}
+		\set{\gamma},
+		 \Pred_Q,  
+		\Post_Q}
+	{\ostate{s_{i}^{i\in L_Q}} \OTWeakarrow {\alpha_Q}
+		\ostate{{s'}_{i}^{\, i\in L_Q}}}
 }%\]
@@
 \begin{mathpar}
-J_Q=\displaystyle{\bigcup_{p=0}^nJ_{p}}
-\qquad
-\Pred\,'=\Pred\land \bigwedge_{p=0}^{n}(\alpha_p=\beta_p\land \Pred_p)\bigotimes_{i=0}^{p-1}\Post_i
+%J_Q=\displaystyle{\bigcup_{t=0}^nJ_{t}}
+%\qquad
+\Pred\,'=\Pred\land (\beta_{j_0}=\alpha_Q\land \Pred_Q)
 \\
-\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}}\text{\quad and\quad}
-\Post\,'=\Post\uplus\bigotimes_{p=0}^{n}
-		\Post_p 
+%\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
+\Post\,'=\Post\uplus\Post_Q
 \end{mathpar}
@@
 		{
-			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
+			\set{\gamma}\uplus\vis{\beta_j^{j\in J\setminus \{j_0\}}}, 
 			\Pred\,',  \Post\,'
@@
 \end{lemma}
-\TODO{Proof starts from here}
-
-\begin{proof} Suppose we have:
-\begin{mathpar}
-%\[
-P\models{\openrule
-	{
-		\gamma_j^{j\in J}, 
-		\Pred,  
-		\Post}
-	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
-		\ostate{s_i'^{\, i\in L}}}
-}
-\end{mathpar}
-By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
-$\forall p\!\in\![0..m_1].P\models\openrule
-    {\set{\beta^1_p},\Pred^1_p,\Post^1_p   }
-         {\ostate{{(s^1_{pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s^1_{(p+1)i})}^{i\in L}}} \wedge
-P\models\openrule
-         {\set{\beta^2},\Pred^2,\Post^2 }
-         {\ostate{({s_{0i}^2})^{i\in L}} \OTarrow {\alpha} \ostate{({s_{1i}^2})^{i\in L}}}
-\wedge\\
-\forall p \in [0..m_2].P\models\openrule
-         {
-           \set{\beta^3_p},\Pred^3_p, \Post^3_p}
-         { \ostate{(s^3_{pi})^{i\in L}} \OTarrow {\tau} \ostate{(s^3_{(p+1)i})^{i\in L}}}$ 
-\\
-where for all $i\in L$:\\
-$s_i=s^1_{0 i} \wedge s^1_{(m_1+1) i}=s^2_{0i} \wedge  s^2_{1i}= s^3_{0 i} \wedge s^3_{(m_2+1) i}=s'_i$\\
-
-$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{p=0}^{m_1} \vis{\set{\beta^1_p}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{p=0}^{m_2} \vis{\set{\beta^3_p}}}\\
-\Pred=\bigwedge_{p=0}^{m_1}\!\big(\Pred^1_p\bigotimes_{j=0}^{p-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{p=0}^{m_1}\subst{\Post_p^1}\land \bigwedge_{p=0}^{m_2}\!\Pred_p^3\big(\bigotimes_{j=0}^{p-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{p=0}^{m_1}\subst{\Post_p^1}\big)\\
-\Post=\bigotimes_{p=0}^{m_2}\Post^3_p\subst{\Post^2}\bigotimes_{j=0}^{m_1}\subst{\Post^1_j}
-$\\
-
-Note that if $(\beta^i_p)_{j_0}=\tau$ because of Definition \ref{def:Non-ObsTau}, $P$ necessarily makes a $\tau$ open transition and remains in the same state, ($s_p = s_{p+1}$).
-Thus without loss of generality, we can bypass such an open transition and obtain another decomposition of the WOT without the open transition that requires ${\beta^i_{p{j_0}}}=\tau$.
-We can thus  suppose that for all $p$ and $i$ we have ${\beta^i_{p{j_0}}}\neq\tau$.
-
-Moreover, we have for all $p\in[0..n]$:
-\begin{mathpar}
-Q\models{\openrule
-	{
-		\gamma_{p j}^{j\in J_p},
-		 \Pred_p,  
-		\Post_p}
-	{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
-		\ostate{s_{(p+1) i}^{\, i\in L_Q}}}
-}		
-\end{mathpar}
-%In the same way,  by Lemma \ref{lem-rel-OT-WOT} we can decompose $\WOT_p$ into  a series of $m'+n'$ tau open transitions and a single observable open transition:
-%\[Q\models{\openrule
-%			{
-%				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred'^{2}}},  
-%				{{\Post'^{2}}}}
-%				{\ostate{s_{p i}^{i\in L_Q}} \OTarrow {\alpha_p}
-%				\ostate{s_{(p+1) i}^{i\in L_Q}}}
-%				}%\]
-%\]
-
-We proceed by iteration on the list of  OTs of $P$ identified above, these OTs are of the form:
-
-$P\!\models		
-\openrule
-    {
-       {(\beta^i_{p j})^{j\in J}},\Pred_p,\Post_p   }
-         {\ostate{s^{i\in L}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L}_{(p+1)i}}}$
-
-We use an additional variable $t$, in the iteration, it will be used as an index from $0$ to $n$, i.e. inside the OTs of $Q$.
-At the beginning $t=0$, i.e. $Q$ is at state $\ostate{s_{0}}$. \TODO{on peut remplacer $s_t$ par $s_{t i}^{i\in L_Q}$}
-For each step of the iteration, we have two cases:
-\begin{itemize}
-\item If $j_0\in J$ then Q moves by one open transition. By the hypothesis above $\beta^i_{p j_0}\neq \tau$. Additionally, we have 
-$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{p=0}^{m_1} \vis{\set{\beta^1_p}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{p=0}^{m_2} \vis{\set{\beta^3_p}}}$ and\\
- $\gamma_{j_0}=[\beta_0..\beta_n]$, thus
-  $\beta^i_{p j_0}=\beta_t$ with  for some $t$ such that $t$ has value $0$ at beginning and that is incremented whenever this condition is satisfied.
-
-On the other hand, by hypothesis we have \TODO{on peut remplacer $s_t$ par $s_{t i}^{i\in L_Q}$}:
-\[Q\models{\openrule
-	{
-		\gamma_{t j}^{j\in J_t},
-		 \Pred_t,  
-		\Post_t}
-	{ \ostate{s_{t}}\OTWeakarrow {\alpha_t}
-		\ostate{s_{{(t+1)}}}}
-}
-\]
-By  Lemma \ref{lem-rel-OT-WOT} we can decompose this $\WOT$ into  a series of $k+1$ and $k'+1$ tau open transitions and an observable open transition:
+\begin{proof}
+By  Lemma \ref{lem-rel-OT-WOT} we can decompose the WOT of $Q$ into  a series of $k+1$ and $k'+1$ tau open transitions and an observable open transition:
 
@@
 		\Post^2}
-	{\ostate{s^2_{0}}\OTarrow {\alpha_t}
+	{\ostate{s^2_{0}}\OTarrow {\alpha_Q}
 		\ostate{s^2_{1}}}
@@
 such that 
-$s_t=s^1_{0} \wedge s^1_{(k+1) i}=s^2_{0} \wedge  s^2_{1}= s^3_{0} \wedge s^3_{(k'+1) i}=s_{t+1}$\\
-
-$\displaystyle{\gamma_{t j}^{j\in J_t}=\mybigdotcup_{h=0}^{k} \vis{\set{\beta^1_h}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{h=0}^{k'} \vis{\set{\beta^3_h}}}\\
-\Pred_t=\bigwedge_{h=0}^{k}\!\big(\Pred^1_h\bigotimes_{j=0}^{h-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{h=0}^{k}\subst{\Post_h^1}\land \bigwedge_{h=0}^{k'}\!\Pred_h^3\big(\bigotimes_{j=0}^{h-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{h=0}^{k}\subst{\Post_h^1}\big)\\
-\Post=\bigotimes_{h=0}^{k'}\Post^3_h\subst{\Post^2}\bigotimes_{j=0}^{k}\subst{\Post^1_j}
+$s_i^{i\in L_Q}=s^1_{0} \wedge s^1_{(k+1) i}=s^2_{0} \wedge  s^2_{1}= s^3_{0} \wedge s^3_{(k'+1) i}={s'}_i^{i\in L_Q}$\\
+
+$\displaystyle{\set{\gamma}=\mybigdotcup_{h=0}^{k} \vis{\set{\beta^1_h}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{h=0}^{k'} \vis{\set{\beta^3_h}}}
+\\
+\Pred_Q=\bigwedge_{h=0}^{k}\!\big(\Pred^1_h\bigotimes_{j=0}^{h-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{h=0}^{k}\subst{\Post_h^1}\land \bigwedge_{h=0}^{k'}\!\Pred_h^3\big(\bigotimes_{j=0}^{h-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{h=0}^{k}\subst{\Post_h^1}\big)
+\\
+\Post_Q=\bigotimes_{h=0}^{k'}\Post^3_h\subst{\Post^2}\bigotimes_{j=0}^{k}\subst{\Post^1_j}
 $
@@
 \item For the first $k$ open tau transitions, by Definition \ref{def:Non-ObsTau} $P$ can necessarily make a tau open transition if the hole indexed $j_0$ makes a tau action.
-So by Lemma \ref{lem-compose} we obtain $k$ open transitions in the form: \TODO{remarquer la notation compliquee ou trouver une meilleure notation mais pas trop lourde}
+So by Lemma \ref{lem-compose} we obtain $k$ open transitions in the form:
 \[P[Q]_{j_0}\!\models		
@@
        \set{\beta^1_h},{\Pred^1_h},{\Post^1_h}   }
-         {\ostate{s^1_h\uplus s^{i\in L}_{pi} } \OTarrow {\tau} \ostate{s^1_{h+1}\uplus s^{i\in L}_{pi}}}\]
-
-\item For the observable open transition.  By Lemma \ref{lem-compose} we obtain:\\ 
+         {\ostate{s^1_h\uplus s^{i\in L}_{i} } \OTarrow {\tau} \ostate{s^1_{h+1}\uplus s^{i\in L}_{i}}}\]
+
+\item For the observable open transition.  By Lemma \ref{lem-compose} with the lemma hypotheses we obtain:\\ 
 	\[ P[Q]_{j_0}  
@@
 			{\beta^i_{p j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}, 
-			\Pred_p\land\Pred^2\land \alpha_t=\beta^i_{p j_0 },  
-			\Post_p\uplus \Post^2}
-{\ostate{s^{i\in L}_{pi}\uplus s_0^2} \OTarrow {\alpha_p} \ostate{s^{i\in L}_{(p+1)i}\uplus s_1^2}}
+			\Pred\land\Pred^2\land \alpha_t=\beta^i_{p j_0 },  
+			\Post\uplus \Post^2}
+{\ostate{s^{i\in L}_{i}\uplus s_0^2} \OTarrow {\alpha_p} \ostate{{s'}^{i\in L}_{i}\uplus s_1^2}}
 	}
@@
 
+By Lemma \ref{lem-rel-OT-WOT} from cases $(1)$, $(2)$ and $(3)$ we obtain: 
+\[P[Q]_{j_0}\!\models		
+\openrule
+    {
+\set{\gamma'}, \Pred_c,
+\Post_c}
+         {\ostate{s^1_0\uplus s^{i\in L}_{i}} \OTWeakarrow {\alpha^l} 
+	\ostate{{{s'}^{i\in L}_{i}\uplus s_{k'}^3}}}\] 
+where
+\[\set{\gamma'}=\mybigdotcup_{h=0}^k\vis{\set{\beta^1_h}} \dotcup \vis{{\beta^i_{p j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'}\vis{\set{\beta^3_h}}\]
+\[
+\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred^1_h}\subst{\bigotimes_{i=0}^{h-1}\Post_i^1}\land
+\left(Pred\land\Pred^2\land \alpha_t=\beta^i_{p j_0 }\right)\subst{\bigotimes_{i=0}^{k}{\Post_i^1}}\land\\\displaystyle
+\bigwedge_{h=0}^{k'}{\Pred^3_h}\subst{\bigotimes_{i=0}^{h-1}{\Post_i^3}\otimes({\Post\uplus \Post^2})\otimes\bigotimes_{i=0}^{k}{\Post_i^1}}
+\end{array}
+\]
+
+\[\Post_c=(\bigotimes_{i=0}^{k'}{\Post_i^3})\otimes({\Post\uplus \Post^2})\otimes\bigotimes_{i=0}^{k}{\Post_i^1}
+\]
+Note that we have $s_t=s^1_{0} \wedge s^1_{(k+1) i}=s^2_{0} \wedge  s^2_{1}= s^3_{0} \wedge s^3_{(k'+1) i}=s_{t+1}$
+\end{proof}
+
+\begin{lemma}[Weak open transition composition]\label{lem-Weakcompose} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
+	Suppose $j_0\in J$ and $\gamma_{j_0}=[\beta_0..\beta_n]$ and additionally:\\[-2ex]
+\begin{mathpar}
+%\[
+P\models{\openrule
+	{
+		\gamma_j^{j\in J}, 
+		\Pred,  
+		\Post}
+	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
+		\ostate{s_i'^{\, i\in L}}}
+}\\
+\text{~~and for all $t\in[0..n]$~~}
+Q\models{\openrule
+	{
+		\gamma_{t j}^{j\in J_t},
+		 \Pred_t,  
+		\Post_t}
+	{\ostate{s_{t i}^{i\in L_Q}} \OTWeakarrow {\alpha_t}
+		\ostate{s_{(t+1) i}^{\, i\in L_Q}}}
+}%\]
+\end{mathpar}
+Let 
+\begin{mathpar}
+J_Q=\displaystyle{\bigcup_{t=0}^nJ_{t}}
+\qquad
+\Pred\,'=\Pred\land \bigwedge_{t=0}^{n}(\alpha_t=\beta_t\land \Pred_t)\bigotimes_{i=0}^{t-1}\Post_i
+\\
+\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
+\Post\,'=\Post\uplus\bigotimes_{t=0}^{n}
+		\Post_t
+\end{mathpar}
+Then, we have\\[-2ex]
+	\[ P[Q]_{j_0}  
+	\models
+	{\openrule
+		{
+			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
+			\Pred\,',  \Post\,'
+			 }
+		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
+			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
+	}
+	\]
+\end{lemma}
+\TODO{Proof starts from here}
+
+\begin{proof} Suppose we have:
+\begin{mathpar}
+%\[
+P\models{\openrule
+	{
+		\gamma_j^{j\in J}, 
+		\Pred,  
+		\Post}
+	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
+		\ostate{s_i'^{\, i\in L}}}
+}
+\end{mathpar}
+By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
+$\forall p\!\in\![0..m_1].P\models\openrule
+    {\set{\beta^1_p},\Pred^1_p,\Post^1_p   }
+         {\ostate{{(s^1_{pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s^1_{(p+1)i})}^{i\in L}}} \wedge
+P\models\openrule
+         {\set{\beta^2},\Pred^2,\Post^2 }
+         {\ostate{({s_{0i}^2})^{i\in L}} \OTarrow {\alpha} \ostate{({s_{1i}^2})^{i\in L}}}
+\wedge\\
+\forall p \in [0..m_2].P\models\openrule
+         {
+           \set{\beta^3_p},\Pred^3_p, \Post^3_p}
+         { \ostate{(s^3_{pi})^{i\in L}} \OTarrow {\tau} \ostate{(s^3_{(p+1)i})^{i\in L}}}$ 
+\\
+where for all $i\in L$:\\
+$s_i=s^1_{0 i} \wedge s^1_{(m_1+1) i}=s^2_{0i} \wedge  s^2_{1i}= s^3_{0 i} \wedge s^3_{(m_2+1) i}=s'_i$\\
+
+$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{p=0}^{m_1} \vis{\set{\beta^1_p}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{p=0}^{m_2} \vis{\set{\beta^3_p}}}\\
+\Pred=\bigwedge_{p=0}^{m_1}\!\big(\Pred^1_p\bigotimes_{j=0}^{p-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{p=0}^{m_1}\subst{\Post_p^1}\land \bigwedge_{p=0}^{m_2}\!\Pred_p^3\big(\bigotimes_{j=0}^{p-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{p=0}^{m_1}\subst{\Post_p^1}\big)\\
+\Post=\bigotimes_{p=0}^{m_2}\Post^3_p\subst{\Post^2}\bigotimes_{j=0}^{m_1}\subst{\Post^1_j}
+$\\
+
+Note that, for $l\in\{1,2,3\}$ if $(\beta^l_p)_{j_0}=\tau$ because of Definition \ref{def:Non-ObsTau}, $P$ necessarily makes a $\tau$ open transition and remains in the same state, ($s_p = s_{p+1}$).
+Thus without loss of generality, we can bypass such an open transition and obtain another decomposition of the WOT without the open transition that requires ${\beta^l_{p{j_0}}}=\tau$.
+We can thus  suppose that for all $p$ and $l$ we have ${\beta^l_{p{j_0}}}\neq\tau$.
+
+Moreover, we have for all $t\in[0..n]$:
+\begin{mathpar}
+Q\models{\openrule
+	{
+		\gamma_{t j}^{j\in J_t},
+		 \Pred_t,  
+		\Post_t}
+	{\ostate{s_{t i}^{i\in L_Q}} \OTWeakarrow {\alpha_t}
+		\ostate{s_{(t+1) i}^{\, i\in L_Q}}}
+}		
+\end{mathpar}
+%In the same way,  by Lemma \ref{lem-rel-OT-WOT} we can decompose $\WOT_p$ into  a series of $m'+n'$ tau open transitions and a single observable open transition:
+%\[Q\models{\openrule
+%			{
+%				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred'^{2}}},  
+%				{{\Post'^{2}}}}
+%				{\ostate{s_{p i}^{i\in L_Q}} \OTarrow {\alpha_p}
+%				\ostate{s_{(p+1) i}^{i\in L_Q}}}
+%				}%\]
+%\]
+
+We proceed by iteration on the list of  OTs of $P$ identified above, these OTs are of the form, for $l\in\{1,2,3\}$: 
+\[P\!\models		
+\openrule
+    {
+       {(\beta^l_{p j})^{j\in J}},\Pred_p,\Post_p   }
+         {\ostate{s^{i\in L}_{pi}} \OTarrow {\alpha^l} \ostate{s^{i\in L}_{(p+1)i}}}\]
+with $\alpha^2=\alpha$ and $\alpha^1=\alpha^3=\tau$
+
+We use an additional variable $t$, in the iteration, it will be used as an index from $0$ to $n$, i.e. inside the OTs of $Q$.
+At the beginning $t=0$, i.e. $Q$ is at state $\ostate{s_{0}}$. \TODO{on peut remplacer $s_t$ par $s_{t i}^{i\in L_Q}$}
+For each step of the iteration, we have two cases:
+\begin{itemize}
+\item If $j_0\in J$ then Q moves by one open transition. By the hypothesis above $\beta^i_{p j_0}\neq \tau$. Additionally, we have 
+$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{p=0}^{m_1} \vis{\set{\beta^1_p}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{p=0}^{m_2} \vis{\set{\beta^3_p}}}$ and\\
+ $\gamma_{j_0}=[\beta_0..\beta_n]$, thus
+  $\beta^i_{p j_0}=\beta_t$ with  for some $t$ such that $t$ has value $0$ at beginning and that is incremented whenever this condition is satisfied.
+
+On the other hand, by hypothesis we have \TODO{on peut remplacer $s_t$ par $s_{t i}^{i\in L_Q}$}:
+\[Q\models{\openrule
+	{
+		\gamma_{t j}^{j\in J_t},
+		 \Pred_t,  
+		\Post_t}
+	{ \ostate{s_{t}}\OTWeakarrow {\alpha_t}
+		\ostate{s_{{(t+1)}}}}
+}
+\]
+By  Lemma \ref{lem-rel-OT-WOT} we can decompose this $\WOT$ into  a series of $k+1$ and $k'+1$ tau open transitions and an observable open transition:
+
+\[\forall h\!\in\![0..k].Q\models\openrule
+    {\set{\beta^1_h},\Pred^1_h,\Post^1_h   }
+         {\ostate{{(s^1_{h})}} \OTarrow {\tau} \ostate{{(s^1_{(h+1)})}}}
+\]
+
+\[Q\models{\openrule
+	{
+		\set{\beta^2},
+		 \Pred^2,  
+		\Post^2}
+	{\ostate{s^2_{0}}\OTarrow {\alpha_t}
+		\ostate{s^2_{1}}}
+}
+\]
+
+\[
+\forall h \in [0..k'].Q\models\openrule
+         {
+           \set{\beta^3_h},\Pred^3_h, \Post^3_h}
+         { \ostate{(s^3_h)} \OTarrow {\tau} \ostate{(s^3_{(h+1)})}} \]
+
+such that 
+$s_t=s^1_{0} \wedge s^1_{(k+1) i}=s^2_{0} \wedge  s^2_{1}= s^3_{0} \wedge s^3_{(k'+1) i}=s_{t+1}$\\
+
+$\displaystyle{\gamma_{t j}^{j\in J_t}=\mybigdotcup_{h=0}^{k} \vis{\set{\beta^1_h}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{h=0}^{k'} \vis{\set{\beta^3_h}}}\\
+\Pred_t=\bigwedge_{h=0}^{k}\!\big(\Pred^1_h\bigotimes_{j=0}^{h-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{h=0}^{k}\subst{\Post_h^1}\land \bigwedge_{h=0}^{k'}\!\Pred_h^3\big(\bigotimes_{j=0}^{h-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{h=0}^{k}\subst{\Post_h^1}\big)\\
+\Post=\bigotimes_{h=0}^{k'}\Post^3_h\subst{\Post^2}\bigotimes_{j=0}^{k}\subst{\Post^1_j}
+$
+
+\begin{enumerate}
+
+\item For the first $k$ open tau transitions, by Definition \ref{def:Non-ObsTau} $P$ can necessarily make a tau open transition if the hole indexed $j_0$ makes a tau action.
+So by Lemma \ref{lem-compose} we obtain $k$ open transitions in the form: \TODO{remarquer la notation compliquee ou trouver une meilleure notation mais pas trop lourde}
+\[P[Q]_{j_0}\!\models		
+\openrule
+    {
+       \set{\beta^1_h},{\Pred^1_h},{\Post^1_h}   }
+         {\ostate{s^1_h\uplus s^{i\in L}_{pi} } \OTarrow {\tau} \ostate{s^1_{h+1}\uplus s^{i\in L}_{pi}}}\]
+
+\item For the observable open transition.  By Lemma \ref{lem-compose} we obtain:\\ 
+	\[ P[Q]_{j_0}  
+	\models
+	{\openrule
+		{
+			{\beta^i_{p j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}, 
+			\Pred_p\land\Pred^2\land \alpha_t=\beta^i_{p j_0 },  
+			\Post_p\uplus \Post^2}
+{\ostate{s^{i\in L}_{pi}\uplus s_0^2} \OTarrow {\alpha_p} \ostate{s^{i\in L}_{(p+1)i}\uplus s_1^2}}
+	}
+	\]
+
+%
+%\[P[Q]_{j_0}\!\models		
+%\openrule
+%    {
+%       {\beta^i_{p j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2},{\Pred_p}\!\!'',{\Post_p}\!\!''   }
+%         {\ostate{s^{i\in L \uplus L_Q}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L\uplus L_Q }_{(p+1)i}}}\] \\
+% such that  ${\Pred_p}\!\!'' \iff {\Pred_p}
+%		\land {\Pred_p}\!\!'\land \alpha_t=\beta_{j_0}$, ${\Post_p}\!\!''={\Post_p}\uplus 
+%		{\Post_p}\!\!'$\\ 
+\item We proceed in the same way as the first item for $k'$ last weak open transitions, and we obtain $k'$ open tau transitions.\\
+\end{enumerate}
+
 By Lemma \ref{lem-rel-OT-WOT} from cases $(1)$, $2$ and $(3)$ we obtain: 
@@
     {
-       \beta_p^{(p\in J\setminus\{j_0\}) \uplus J_Q}, {\Pred_p}
-		\land {\Pred_p}\!\!'\land \alpha_p'=\beta_{j_0}$, ${\Post_p}\!\!''={\Post_p}\uplus 
-		{\Post_p}\!\!'}
-         {\ostate{s^{i\in L\uplus L_Q}_{pi}} \OTWeakarrow {\alpha} \ostate{s^{i\in L \uplus L_Q}_{(p+1)i}}}\]
-
- \item Else, $j_0\not\in J$. $t$ does not move  and $Q$ does not move, i.e. we have: $\ostate{(s_{ti})^{i\in L_Q}} = \ostate{({s}_{(t+1)i})^{i\in L_Q}}$....
+\set{\gamma}, \Pred_c,
+\Post_c}
+         {\ostate{s^1_0\uplus s^{i\in L}_{pi}} \OTWeakarrow {\alpha^l} 
+	\ostate{{s^{i\in L}_{(p+1)i}\uplus s_{k'}^3}}}\] 
+where
+\[\set\gamma=\mybigdotcup_{h=0}^k\vis{\set{\beta^1_h}} \dotcup \vis{{\beta^i_{p j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'}\vis{\set{\beta^3_h}}\]
+\[
+\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred^1_h}\subst{\bigotimes_{i=0}^{h-1}\Post_i^1}\land
+\left(Pred_p\land\Pred^2\land \alpha_t=\beta^i_{p j_0 }\right)\subst{\bigotimes_{i=0}^{k}{\Post_i^1}}\land\\\displaystyle
+\bigwedge_{h=0}^{k'}{\Pred^3_h}\subst{\bigotimes_{i=0}^{h-1}{\Post_i^3}\otimes({\Post_p\uplus \Post^2})\otimes\bigotimes_{i=0}^{k}{\Post_i^1}}
+\end{array}
+\]
+
+\[\Post_c=(\bigotimes_{i=0}^{k'}{\Post_i^3})\otimes({\Post_p\uplus \Post^2})\otimes\bigotimes_{i=0}^{k}{\Post_i^1}
+\]
+Note that we have $s_t=s^1_{0} \wedge s^1_{(k+1) i}=s^2_{0} \wedge  s^2_{1}= s^3_{0} \wedge s^3_{(k'+1) i}=s_{t+1}$
+
+ \item Else, $j_0\not\in J$. $t$ does not move  and $Q$ does not move, i.e. we have: $\ostate{(s_{t})} = \ostate{({s}_{(t+1)})}$
+By lemma~\ref{lem-compose-2} we have:
+\[P[Q]_{j_0}\!\models		
+\openrule
+    {
+       {(\beta^l_{p j})^{j\in J}},\Pred_p,\Post_p   }
+         {\ostate{s^{i\in L}_{pi}\uplus s_t} \OTarrow {\alpha^l} \ostate{s^{i\in L}_{(p+1)i}\uplus s_t}}
+\]
+and thus
+\[P[Q]_{j_0}\!\models		
+\openrule
+    {
+       \vis{{(\beta^l_{p j})^{j\in J}}},\Pred_p,\Post_p   }
+         {\ostate{s^{i\in L}_{pi}\uplus s_t} \OTWeakarrow {\alpha^l} \ostate{s^{i\in L}_{(p+1)i}\uplus s_t}}
+\]
+
 \end{itemize}

### 2019-04-24 2016-Weak-FH-Bisim/WeakBisim.tex
Big changes

@@
 \TODO{voisr si on redefinit les bigotimes pour prendre des maps et retourner des maps au lieu des substitutions (et on englobe dans une subst a la fin)}
+
+\TODO{prendre soin des posts sur les actions partout}
 
@@
 	\end{itemize}
+
+We take in this article a semantics and logical understanding of these automata.
+Open automata are closed by a simple form of refinement that allows us to refine the predicate, or substitute any free variable by an expression.
+More formally, let $\Post$ be any substitution and $\Pred$ any predicate suppose $\vars(t)\cap \dom(\Post)=\emptyset$ and $\vars(t')\cap \dom(\Post)=\emptyset$.
+Then we have the following implication:
+
+	 \begin{mathpar}
+    \openrule
+         {
+           \set{\beta}, \Pred\,',\Post\,'}
+          {t \OTarrow {\alpha} t'}\in\mathcal{T}
+\implies
+    \openrule
+         {
+           \set{\beta}\subst{\Post}, \Pred\,'\subst{\Post}\land\Pred,\Post\otimes\Post\,'}
+         {t \OTarrow {\alpha\subst{\Post}} {t'}}\in\mathcal{T}
+\end{mathpar}
 \end{definition}
@@
    \mathcal{T}_1\!>$ and $A_2 = <\!J,\mathcal{S}_2,t_0, \mathcal{T}_2\!>$
-   are open automata with identical holes of the same sort.
+   are open automata with identical holes of the same sort, with disjoint state variables.
 
@@
      \land \alpha\!=\!\alpha_x \land  
-     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
+     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)$
      %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
@@
      \land \alpha\!=\!\alpha_x \land  
-     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
+     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)$
      %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
      %     \right)$.
-
-\medskip
-
-Idea: we define $OT\implies OT$ to check whether an OT is a particular case of another one (refining free action variables and predicates)
- \begin{mathpar}
-    \openrule
-         {
-           \beta_{j}^{j\in J_{x}}, \Pred_{OT},\subst{x_k\leftarrow e_k}^{k\in K}}
-          {t \OTarrow {\alpha} t'}\in\mathcal{T}
-\implies
-    \openrule
-         {
-           (\beta_{j}\Post)^{j\in J}, \Pred_{OT}\Post\land\Pred,\subst{x_k\leftarrow e_k\Post}^{k\in K}}
-         {t \OTarrow {\alpha\Post} {t'}}\in\mathcal{T}
-\end{mathpar}
-
-\medskip
 
@@
  \end{definition}
-Classically, $\Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}$
+Classically, $\Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}$
 applies in parallel the  
@@
     		\ostate{s_m'}} }\\\\
-%     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J \frac{num}{den}	\\
+    J' = \biguplus_{m\in I_1}\!\! J_m \uplus J	\\
     	\Pred = \bigwedge_{m\in I_1\uplus I_2}\!\! \Pred_m \land
@@
     	\forall i\in	L\backslash \left(\biguplus_{m\in I_1}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
-    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
+    \fresh(\alpha'_m,\alpha',\beta_j^{j\in J},\alpha) 
     }
@@
     		{
-    		{\beta_j}^{j\in J^\prime}, \Pred,  \biguplus_{m\in I_1\uplus I_2} 
+    		\beta_j^{j\in J^\prime}, \Pred,  \biguplus_{m\in I_1\uplus I_2} 
     		\Post_m}
@@
          {
-           \set{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
+           \set{\gamma_3},\Pred_3,\Post_3  }
          {s_2 \OTWeakarrow {\tau} s'} \in\WT
 \\
-\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
-}
-{
-\openrule
-         {
-           \set{\gamma_1}\dotcup \set{\gamma_2}\dotcup\set{\gamma_3},
+\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land \Pred_3\subst{\Post_2\otimes\Post_1}
+\\
+\set{\gamma}=\set{\gamma_1}\dotcup \set{\gamma_2}\subst{\Post_1}\dotcup\set{\gamma_3}\subst{\Post_2\otimes \Post_1}\\
+\alpha'=\alpha\subst{\Post_1}
+}
+{
+\openrule
+         {\set{\gamma}
+           ,
 		\Pred,
-				({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K} } 
-         {s \OTWeakarrow {\alpha} s'} \in\WT
+				\Post_3\otimes\Post_2\otimes\Post_1} 
+         {s \OTWeakarrow {\alpha'} s'} \in\WT
 } \WTTrois
@@
 Let $A_1 = <J,\mathcal{S}_1, s_0,
-    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata.
+    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata with disjoint state variables.
 Let $<J,\mathcal{S}_1, s_0,
@@
      \land \alpha\!=\!\alpha_x \land  
-     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$
+     \Pred_{s',t_x}\subst{\Post_{OT}\otimes\Post_{OT_x}}\right)$
 
@@
 		{
-			{\beta^i_{p j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}, 
-			\Pred\land\Pred^2\land \alpha_t=\beta^i_{p j_0 },  
+			{\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}, 
+			\Pred\land\Pred^2\land \alpha_Q=\beta_{j_0 },  
 			\Post\uplus \Post^2}
-{\ostate{s^{i\in L}_{i}\uplus s_0^2} \OTarrow {\alpha_p} \ostate{{s'}^{i\in L}_{i}\uplus s_1^2}}
+{\ostate{s^{i\in L}_{i}\uplus s_0^2} \OTarrow {\alpha} \ostate{{s'}^{i\in L}_{i}\uplus s_1^2}}
 	}
@@
 \Post_c}
-         {\ostate{s^1_0\uplus s^{i\in L}_{i}} \OTWeakarrow {\alpha^l} 
-	\ostate{{{s'}^{i\in L}_{i}\uplus s_{k'}^3}}}\] 
+         {\ostate{s^1_0\uplus s^{i\in L}_{i}} \OTWeakarrow {\alpha} 
+	\ostate{{{s'}^{i\in L}_{i}\uplus s_{k'+1}^3}}}\] 
 where
-\[\set{\gamma'}=\mybigdotcup_{h=0}^k\vis{\set{\beta^1_h}} \dotcup \vis{{\beta^i_{p j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'}\vis{\set{\beta^3_h}}\]
+\[\set{\gamma'}=\mybigdotcup_{h=0}^k\vis{\set{\beta^1_h}} \dotcup \vis{{\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'}\vis{\set{\beta^3_h}}\]
 \[
 \Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred^1_h}\subst{\bigotimes_{i=0}^{h-1}\Post_i^1}\land
-\left(Pred\land\Pred^2\land \alpha_t=\beta^i_{p j_0 }\right)\subst{\bigotimes_{i=0}^{k}{\Post_i^1}}\land\\\displaystyle
+\left(Pred\land\Pred^2\land \alpha_Q=\beta_{j_0 }\right)\subst{\bigotimes_{i=0}^{k}{\Post_i^1}}\land\\\displaystyle
 \bigwedge_{h=0}^{k'}{\Pred^3_h}\subst{\bigotimes_{i=0}^{h-1}{\Post_i^3}\otimes({\Post\uplus \Post^2})\otimes\bigotimes_{i=0}^{k}{\Post_i^1}}
@@
 \]
-Note that we have $s_t=s^1_{0} \wedge s^1_{(k+1) i}=s^2_{0} \wedge  s^2_{1}= s^3_{0} \wedge s^3_{(k'+1) i}=s_{t+1}$
+Note that we have $s_i^{i\in L_Q}=s^1_{0} \wedge s^1_{(k+1) i}=s^2_{0} \wedge  s^2_{1}= s^3_{0} \wedge s^3_{(k'+1) i}={s'}_i^{i\in L_Q}$\\
+
+Note also that $\Post$ only acts on variables of $P$ while $\Post^1_i$ only acts on state variables of $Q$. A
 \end{proof}

### 2019-04-24 2016-Weak-FH-Bisim/WeakBisim.tex
Jusqu a l ennonce de lemma4

@@
 \makeatother
-
+\newcommand{\shortotimes}{\!\otimes\!}
 \usepackage{macrospNets}
@@
 
-\smallskip
-
-We denote $y\gets e$ a substitution. The application of the substitution is denoted
-$\subst{y\gets e}$, the operation replaces in a term all occurrences 
-of the variable $y$ by the expression $e$ (note that the absence of binders makes this operation 
-trivial). 
-We use sets of equations of the form $x_i=e_i$, ranged over by $\Post$; $\subst{\Post}$ is the substitution that applies all the substitutions defined by $\Post$.
-
-\subsubsection*{Indexed sets and substitution}
+\subsubsection*{Indexed sets}
 
@@
 
+\subsubsection*{Substitutions}
+
+We denote $y\gets e$ a substitution. The application of the substitution is denoted
+$\subst{y\gets e}$, the operation replaces in a term all occurrences 
+of the variable $y$ by the expression $e$ (note that the absence of binders makes this operation 
+trivial). 
+We use sets of equations of the form $x_i=e_i$, ranged over by $\Post$; $\subst{\Post}$ is the substitution that applies all the substitutions defined by $\Post$ in a parallel manner.
+$\otimes$ is the composition operator on substitutions: $(x_k\gets e_k)^{k\in K}\shortotimes \Post =  (x_k\gets e_k\subst{\Post})^{k\in K}$
+
 \subsection{Parameterised Networks (pNets)}
@@
          {
-           \set{\beta}\subst{\Post}, \Pred\,'\subst{\Post}\land\Pred,\Post\otimes\Post\,'}
+           \set{\beta}\subst{\Post}, \Pred\,'\subst{\Post}\land\Pred,\Post\shortotimes\Post\,'}
          {t \OTarrow {\alpha\subst{\Post}} {t'}}\in\mathcal{T}
@@
 
- $\Pred_{s,t} \land \Pred_{OT}\implies\bigvee_{x\in X} \Pred_x$\\
-and
+ $\Pred_{s,t} \land \Pred_{OT}\implies\bigvee_{x\in X} \Pred_x$
+and\\
 %\hspace{1cm}
@@
 %be a pNet. 
-Consider a synchronisation vector $\symb{SV}$. We 
+Consider a synchronisation vector $\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
+{\alpha'} 
+{e_b}$. We 
 define a
@@
 \\
-\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land \Pred_3\subst{\Post_2\otimes\Post_1}
+\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land \Pred_3\subst{\Post_2\shortotimes\Post_1}
 \\
-\set{\gamma}=\set{\gamma_1}\dotcup \set{\gamma_2}\subst{\Post_1}\dotcup\set{\gamma_3}\subst{\Post_2\otimes \Post_1}\\
+\set{\gamma}=\set{\gamma_1}\dotcup \set{\gamma_2}\subst{\Post_1}\dotcup\set{\gamma_3}\subst{\Post_2\shortotimes \Post_1}\\
 \alpha'=\alpha\subst{\Post_1}
@@
 		\Pred,
-				\Post_3\otimes\Post_2\otimes\Post_1} 
+				\Post_3\shortotimes\Post_2\shortotimes\Post_1} 
          {s \OTWeakarrow {\alpha'} s'} \in\WT
@@
      \land \alpha\!=\!\alpha_x \land  
-     \Pred_{s',t_x}\subst{\Post_{OT}\otimes\Post_{OT_x}}\right)$
+     \Pred_{s',t_x}\subst{\Post_{OT}\shortotimes\Post_{OT_x}}\right)$
 
@@
        		\land \alpha\!=\!\alpha_{pxy} \land
-       		\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
+       		\Pred\,'_{{pxy}}\subst{\Post_{OT}\shortotimes\Post_{OT_{pxy}}}\right)$.
        	\end{small}
@@
        		\land \alpha\!=\!\alpha_{px} \land
-       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\land\Pred_{p,u}\\
+       		\Pred_{{px}}\subst{\Post_{OT}\shortotimes\Post_{OT_{px}}}\right)\land\Pred_{p,u}\\
        		%
@@
        		\land \alpha\!=\!\alpha_{px} \land
-       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\\
+       		\Pred_{{px}}\subst{\Post_{OT}\shortotimes\Post_{OT_{px}}}\right)\\
        		%
@@
        		\land \alpha_{px}\!=\!\alpha_{pxy}\\\hspace{3em}~ \land
-       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\big))
+       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}\shortotimes\Post_{OT_{pxy}}}\big))
        		\land \alpha\!=\!\alpha_{px} \land
-       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\\
+       		\Pred_{{px}}\subst{\Post_{OT}\shortotimes\Post_{OT_{px}}}\big)\\
        		%
@@
        		\land \alpha\!=\alpha_{px}\!=\!\alpha_{pxy}\\\hspace{3em}~ \land
-       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}
+       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}\shortotimes\Post_{OT_{pxy}}}
        		\land
-       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\big)
+       		\Pred_{{px}}\subst{\Post_{OT}\shortotimes\Post_{OT_{px}}}\big)\big)
        		$
@@
 substitutions  and of the predicates, we have:\\
-       	$\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\land 
-       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
+       	$\Pred_{{px}}\subst{\Post_{OT}\shortotimes\Post_{OT_{px}}}\land 
+       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}\shortotimes\Post_{OT_{pxy}}}\\
        	\Leftrightarrow % we changed =
-       	\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land
-       	\Pred_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
-       	\implies\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
+       	\Pred_{{px}}\subst{\Post_{OT}\shortotimes\Post_{OT_{px}}\shortotimes\Post_{OT_{pxy}}}\land
+       	\Pred_{{pxy}}\subst{\Post_{OT}\shortotimes\Post_{OT_{px}}\shortotimes\Post_{OT_{pxy}}}\\
+       	\implies\Pred\,'_{{pxy}}\subst{\Post_{OT}\shortotimes\Post_{OT_{px}}\shortotimes\Post_{OT_{pxy}}}\\
        	\Leftrightarrow % we changed = 
-       	 \Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}} $\\
+       	 \Pred\,'_{{pxy}}\subst{\Post_{OT}\shortotimes\Post_{OT_{pxy}}} $\\
 
@@
 \land \alpha\!=\alpha_{px}\!=\!\alpha_{pxy}\\~\hspace{3em}~ \land
-\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\big)\big)
+\Pred\,'_{{pxy}}\subst{\Post_{OT}\shortotimes\Post_{OT_{pxy}}}\big)\big)
 \\
@@
 \land \alpha\!=\!\alpha_{pxy} \land
-\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
+\Pred\,'_{{pxy}}\subst{\Post_{OT}\shortotimes\Post_{OT_{pxy}}}\right)$.
   \end{small}
@@
 
-\begin{lemma}[Open transition composition]\label{lem-compose-2} ~\\	Suppose $j_0\not\in J$ and $L_Q=\Leaves({Q})$:\\[-2ex]
+\begin{lemma}[Open transition composition -- inactive]\label{lem-compose-2} ~\\	This lemma is the simple case where the pNet filling the hole is not involved in the transition.
+Suppose $j_0\not\in J$ and $L_Q=\Leaves({Q})$:\\[-2ex]
 \begin{mathpar}
@@
 \end{lemma}
+The proof is trivial.
 
@@
  \land \alpha_Q\!=\!\alpha_x \land  
- \Pred_{s x}\subst{\Post\,''}\subst{\Post_{OT_x}}\right)$
+ \Pred_{s x}\subst{\Post\,''\shortotimes\Post_{OT_x}}\right)$
 
@@
  	\land \alpha_Q\!=\!\alpha_x \land  
- 	\Pred_{s x}\subst{\Post\,''}\subst{\Post_{OT_x}}\right)
+ 	\Pred_{s x}\subst{\Post\,''\shortotimes\Post_{OT_x}}\right)
  }
@@
  		\land \alpha_Q\!=\!\alpha_x \land \alpha_Q\!=\!\beta_{j_0 x} \land  
- 		\Pred_{s x}\subst{\Post\,''}\subst{\Post_{OT_x}}\right)
+ 		\Pred_{s x}\subst{\Post\,''\shortotimes\Post_{OT_x}}\right)
  	}
@@
  	\item Concerning the last term, we need 
- 	$\Pred_{s x}\subst{\Post_{OT}}\subst{\Post\,'\uplus \Post_{OT_x}}$ 
+ 	$\Pred_{s x}\subst{\Post_{OT}\shortotimes(\Post\,'\uplus \Post_{OT_x})}$ 
  	, i.e.:
- 	$\Pred_{s x}\subst{\Post\,'\uplus 
- 		\Post\,''}\subst{\Post\,'\uplus \Post_{OT_x}}$. We 
+ 	$\Pred_{s x}\subst{(\Post\,'\uplus 
+ 		\Post\,'')\shortotimes(\Post\,'\uplus \Post_{OT_x})}$. We 
  	can conclude by observing that	$\Pred_{s x}$ does not use any variable of $P$ 
- 	and thus $\subst{Post\,'}$ has no effect.
+ 	and thus the substitution $\subst{Post\,'}$ has no effect on it.
  \end{itemize}	
@@
  		 \land \alpha_Q\!=\!\beta_{j_0 x}\right) \land \alpha_Q\!=\!\alpha_x\land  
- 		\Pred_{s x}\subst{\Post\,''}\subst{\Post_{OT_x}}\right)
+ 		\Pred_{s x}\subst{\Post\,''\shortotimes\Post_{OT_x}}\right)
  	}\]
@@
 			\land \alpha\!=\!\alpha_x \land  
-			\Pred_{s x}\subst{\Post\,'}\subst{\Post_{OT_x}}\right)$
+			\Pred_{s x}\subst{\Post\,'\shortotimes\Post_{OT_x}}\right)$
 			%     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x}) \right)$.
@@
 \land \alpha\!=\!\alpha_x}} %\\ \hspace*{40mm} %
-\land \Pred_{s x}\subst{\Post\,'}\subst{\Post_{OT_x}}) \land
+\land \Pred_{s x}\subst{\Post\,'\shortotimes\Post_{OT_x}}) \land
 \Pred\,''\\ % 
@@
 \Pred\,''
-\land \alpha_Q=\beta_{j_0 x}\right)
+\land \alpha_Q\!=\!\beta_{j_0 x}\right)
 \land \alpha\!=\!\alpha_x}} 
-\land \Pred_{s x}\subst{\Post\,'}\subst{\Post_{OT_x}}) 	
+\land \Pred_{s x}\subst{\Post\,'\shortotimes\Post_{OT_x}}) 	
 $\end{small}
@@
 	change the validity of the formula (those variables are not used).
-	\item We need $\Pred_{s x}\subst{\Post_{OT}}\subst{\Post_{OT_x}\uplus \Post\,''}$, i.e.:
-	$\Pred_{s x}\subst{\Post\,'\uplus \Post\,''}\subst{\Post_{OT_x}\uplus \Post\,''}$. We 
+	\item We need $\Pred_{s x}\subst{\Post_{OT}\shortotimes(\Post_{OT_x}\uplus \Post\,'')}$, i.e.:
+	$\Pred_{s x}\subst{(\Post\,'\uplus \Post\,'')\shortotimes(\Post_{OT_x}\uplus \Post\,'')}$. We 
 	can conclude by observing that	$\Pred_{s x}$ does not use any variable of $Q$ 
-	and thus $\subst{\Post\,''}$ has no effect.
+	and thus the substitution involving $\Post\,''$ has no effect.
 \end{itemize}	
@@
 
-\TODO{Voir ou ajouter ceci: We introduce the notation ${\displaystyle \bigotimes_{i=1}^{n} \subst{Post_i}}$ to denote a combination of multiple substitution operations}
-
-${\displaystyle \bigotimes_{i=0}^{n} \subst{Post_i}} = \subst{Post_n}..\subst{Post_0}$
+We use ${\displaystyle \bigotimes_{i=n}^{0} \Post_i}$ to denote  $\Post_n\otimes .. \otimes \Post_0$. By convention ${\displaystyle \bigotimes_{i=-1}^{0} \Post_i}$ is the identity.
+
+\TODO{attention a l ordre: inverse d avant mais colle mieux a la notation -- check everywhere below}
 \subsection{Weak bisimulation is an equivalence}
@@
          {
-           \set{\beta^3_i},\Pred^3_i,({x^3_{ik}\gets e^3_{ik}})^{k\in K_i}    }
+           \set{\beta^3_i},\Pred^3_i,\Post_i^3    }
          {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
@@
 $
-s=s^1_0 \wedge s^1_{n+1}=s_0^2 \wedge s_1^2 = s^3_0 \wedge s^3_{m+1}=s',
-\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i}}}
+s=s^1_0 \wedge s^1_{n+1}=s_0^2 \wedge s_1^2 = s^3_0 \wedge s^3_{m+1}=s',\\
+\displaystyle{
+\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}\subst{\bigotimes_{j=i-1}^{0} \Post_j^1 } }  \dotcup  \vis{\set{\beta^2}\subst{\bigotimes_{j=n}^{0}\Post_j^1}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i} \subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j} }}
 \\
-\Pred=\bigwedge_{i=0}^n\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\land\Pred^2 \bigotimes_{j=0}^{n}\subst{\Post_j^1}\land\\ 
-~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_i^3\bigotimes_{j=0}^{i-1}\subst{\Post_j^3}\subst{\Post^2}\bigotimes_{j=0}^{n}\subst{\Post^1_j}\Big)\\
-\Post=\big({x^3_{mk}\gets e^3_{mk}\bigotimes_{j=0}^{m-1}\subst{\Post_j^3}\subst{\Post^2}\bigotimes_{j=0}^{n}\subst{\Post^1_j}\big)^{k\in K_m}}
+\Pred=\bigwedge_{i=0}^n\Pred^1_i\subst{\bigotimes_{j=i-1}^{0}\Post_j^1}\land\Pred^2 \subst{\bigotimes_{j=n}^{0}\Post_j^1}\land\\ 
+~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_i^3\subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j}\Big)\\
+\Post=\bigotimes_{j=m}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j
 $
@@
 \left(Pred\land\Pred^2\land \alpha_Q=\beta_{j_0 }\right)\subst{\bigotimes_{i=0}^{k}{\Post_i^1}}\land\\\displaystyle
-\bigwedge_{h=0}^{k'}{\Pred^3_h}\subst{\bigotimes_{i=0}^{h-1}{\Post_i^3}\otimes({\Post\uplus \Post^2})\otimes\bigotimes_{i=0}^{k}{\Post_i^1}}
+\bigwedge_{h=0}^{k'}{\Pred^3_h}\subst{\bigotimes_{i=0}^{h-1}{\Post_i^3}\shortotimes({\Post\uplus \Post^2})\shortotimes\bigotimes_{i=0}^{k}{\Post_i^1}}
 \end{array}
@@
 
-\[\Post_c=(\bigotimes_{i=0}^{k'}{\Post_i^3})\otimes({\Post\uplus \Post^2})\otimes\bigotimes_{i=0}^{k}{\Post_i^1}
+\[\Post_c=(\bigotimes_{i=0}^{k'}{\Post_i^3})\shortotimes({\Post\uplus \Post^2})\shortotimes\bigotimes_{i=0}^{k}{\Post_i^1}
 \]
@@
 \left(Pred_p\land\Pred^2\land \alpha_t=\beta^i_{p j_0 }\right)\subst{\bigotimes_{i=0}^{k}{\Post_i^1}}\land\\\displaystyle
-\bigwedge_{h=0}^{k'}{\Pred^3_h}\subst{\bigotimes_{i=0}^{h-1}{\Post_i^3}\otimes({\Post_p\uplus \Post^2})\otimes\bigotimes_{i=0}^{k}{\Post_i^1}}
+\bigwedge_{h=0}^{k'}{\Pred^3_h}\subst{\bigotimes_{i=0}^{h-1}{\Post_i^3}\shortotimes({\Post_p\uplus \Post^2})\shortotimes\bigotimes_{i=0}^{k}{\Post_i^1}}
 \end{array}
@@
 
-\[\Post_c=(\bigotimes_{i=0}^{k'}{\Post_i^3})\otimes({\Post_p\uplus \Post^2})\otimes\bigotimes_{i=0}^{k}{\Post_i^1}
+\[\Post_c=(\bigotimes_{i=0}^{k'}{\Post_i^3})\shortotimes({\Post_p\uplus \Post^2})\shortotimes\bigotimes_{i=0}^{k}{\Post_i^1}
 \]
@@
 %     \symb{sv}_{u(\widetilde{i}k)}\triangleq
-%     <ium_{\widetilde{i}.k}(\widetilde{t})\otimes
-%     -^{\widetilde{I_P}}\otimes
-%     um_{\widetilde{i}.k}(\widetilde{t})\otimes
+%     <ium_{\widetilde{i}.k}(\widetilde{t})\shortotimes
+%     -^{\widetilde{I_P}}\shortotimes
+%     um_{\widetilde{i}.k}(\widetilde{t})\shortotimes
 %  -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
@@
 %$\symb{sv}_{!\widetilde{i}}\triangleq
-%    <um_{\widetilde{i}.k}(\widetilde{t})\otimes
-%    -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\otimes
+%    <um_{\widetilde{i}.k}(\widetilde{t})\shortotimes
+%    -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\shortotimes
 %    -^{\widetilde{I_G}}>\longrightarrow
@@
      \symb{sv}_{u(\widetilde{i}.k)}\triangleq
-     <?um_{\widetilde{i}.k}(\widetilde{t})\otimes
-     -^{\widetilde{I_P}}\otimes
-     !m_{\widetilde{i}.k}(\widetilde{t})\otimes
+     <?um_{\widetilde{i}.k}(\widetilde{t})\shortotimes
+     -^{\widetilde{I_P}}\shortotimes
+     !m_{\widetilde{i}.k}(\widetilde{t})\shortotimes
      -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
@@
 $\symb{sv}_{?\widetilde{i}}\triangleq
-     <?m_{\widetilde{i}.k}(\widetilde{t})\otimes
-     -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\otimes
+     <?m_{\widetilde{i}.k}(\widetilde{t})\shortotimes
+     -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\shortotimes
      -^{\widetilde{I_G}}>\longrightarrow
@@
 $\symb{sv}_{!\widetilde{i}}\triangleq
-    <!um_{\widetilde{i}.k}(\widetilde{t})\otimes
-    -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\otimes
+    <!um_{\widetilde{i}.k}(\widetilde{t})\shortotimes
+    -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\shortotimes
     -^{\widetilde{I_G}}>\longrightarrow
@@
     <?m_{\widetilde{i}.j}^{\forall j\in I_K}(\widetilde{t})
-    \otimes !bm_{\widetilde{i}.k}(\widetilde{t})
-    \otimes -^{\widetilde{I_G}}>\longrightarrow \tau( bm(\widetilde{t}))$ &
+    \shortotimes !bm_{\widetilde{i}.k}(\widetilde{t})
+    \shortotimes -^{\widetilde{I_G}}>\longrightarrow \tau( bm(\widetilde{t}))$ &
     $I_K = \{k/\widetilde{i}.k\in \widetilde{I_{G+P}}\}$, \\ &  &  and
@@
 $\symb{sv}_{?\widetilde{i}}\triangleq
-     <!dm_{\widetilde{i}.k}(\widetilde{t})\otimes
-     -^{\widetilde{I_P}}\otimes
-     ?dm_{\widetilde{i}.k}(\widetilde{t})\otimes
+     <!dm_{\widetilde{i}.k}(\widetilde{t})\shortotimes
+     -^{\widetilde{I_P}}\shortotimes
+     ?dm_{\widetilde{i}.k}(\widetilde{t})\shortotimes
      -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}}
@@
 %      <?m_{\widetilde{i}.k}^{\forall k\in
-%        I_K}(\widetilde{t})\otimes
-%      -^{\widetilde{I_P}}\otimes -^{\widetilde{I_G}}>\longrightarrow
+%        I_K}(\widetilde{t})\shortotimes
+%      -^{\widetilde{I_P}}\shortotimes -^{\widetilde{I_G}}>\longrightarrow
      %      ?m_{\widetilde{i}}(\widetilde{t})$
@@
 $\symb{sv}_{!\widetilde{i}}\triangleq
-    <  ?m_{\widetilde{i}.k}(\widetilde{t})\otimes
-    -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\otimes
+    <  ?m_{\widetilde{i}.k}(\widetilde{t})\shortotimes
+    -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\shortotimes
     -^{\widetilde{I_G}}>\longrightarrow ?m_{\widetilde{i}}(\widetilde{t})$
@@
      $\symb{sv}_{u(\widetilde{i}.k)}\triangleq
-     <Discard\otimes
-     -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\otimes
+     <Discard\shortotimes
+     -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\shortotimes
      -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
@@
      $\symb{sv}_{u(\widetilde{i}.k)}\triangleq
-     <Error\otimes
-     -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\otimes
+     <Error\shortotimes
+     -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\shortotimes
      -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
@@
 %%      \symb{sv}_{u(\widetilde{i}.k)}\triangleq
-%%      <?um_{\widetilde{i}.k}(\widetilde{t})\otimes
-%%      -^{\widetilde{I_P}}\otimes
-%%      !m_{\widetilde{i}.k}(\widetilde{t})\otimes
+%%      <?um_{\widetilde{i}.k}(\widetilde{t})\shortotimes
+%%      -^{\widetilde{I_P}}\shortotimes
+%%      !m_{\widetilde{i}.k}(\widetilde{t})\shortotimes
 %%      -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
@@
 %% $(DM )_{\widetilde{k}}$& $\symb{sv}_{?\widetilde{i}}\triangleq
-%%      <?m_{\widetilde{i}.k}(\widetilde{t})\otimes
+%%      <?m_{\widetilde{i}.k}(\widetilde{t})\shortotimes
 %%      -^{\widetilde{I_{G+P}}
-%%       \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\otimes -^{\widetilde{I_G}}>\longrightarrow
+%%       \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\shortotimes -^{\widetilde{I_G}}>\longrightarrow
 %%      ?m_{\widetilde{i}}(\widetilde{t})$&$\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}\uplus \widetilde{I_P}$\\
@@
 %% $\symb{sv}_{!\widetilde{i}}\triangleq
-%%     <!um_{\widetilde{i}.k}(\widetilde{t})\otimes
+%%     <!um_{\widetilde{i}.k}(\widetilde{t})\shortotimes
 %%     -^{\widetilde{I_P}\uplus
-%%       \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\otimes
+%%       \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\shortotimes
 %%     -^{\widetilde{I_G}}>\longrightarrow
@@
 %%      <?m_{\widetilde{i}.k}^{\forall k\in
-%%        I_K}(\widetilde{t})\otimes
-%%      -^{\widetilde{I_P}}\otimes -^{\widetilde{I_G}}>\longrightarrow
+%%        I_K}(\widetilde{t})\shortotimes
+%%      -^{\widetilde{I_P}}\shortotimes -^{\widetilde{I_G}}>\longrightarrow
 %%      ?m_{\widetilde{i}}(\widetilde{t})$ & $I_K = \{k/\widetilde{i}.k\in \widetilde{I_G}\uplus
@@
 %% $(DM )_{\widetilde{k}}$& $\symb{sv}_{?\widetilde{i}}\triangleq
-%%      <?m_{\widetilde{i}.k}(\widetilde{t})\otimes
+%%      <?m_{\widetilde{i}.k}(\widetilde{t})\shortotimes
 %%      -^{\widetilde{I_P}\uplus
-%%       \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\otimes -^{\widetilde{I_G}}>\longrightarrow
+%%       \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\shortotimes -^{\widetilde{I_G}}>\longrightarrow
 %%      ?m_{\widetilde{i}}(\widetilde{t})$&$\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}\uplus \widetilde{I_P}$\\
@@
 %% $\symb{sv}_{!\widetilde{i}}\triangleq
-%%     <!m_{\widetilde{i}.k}(\widetilde{t})\otimes
-%%     ?m_{\widetilde{i}.g}(\widetilde{t})\otimes -^{\widetilde{I_P}\uplus
-%%       \widetilde{I_G}\backslash\{\widetilde{i}\cdot k,\widetilde{i}\cdot g\}}\otimes
+%%     <!m_{\widetilde{i}.k}(\widetilde{t})\shortotimes
+%%     ?m_{\widetilde{i}.g}(\widetilde{t})\shortotimes -^{\widetilde{I_P}\uplus
+%%       \widetilde{I_G}\backslash\{\widetilde{i}\cdot k,\widetilde{i}\cdot g\}}\shortotimes
 %%     -^{\widetilde{I_G}}>\longrightarrow
@@
 %    <?m_{\widetilde{i}.j}^{\forall j\in I_K}(\widetilde{t})
-%    \otimes !bm_{\widetilde{i}.k}(\widetilde{t})
-%    \otimes -^{\widetilde{I_G}}>\longrightarrow \tau( bm(\widetilde{t}))$,
+%    \shortotimes !bm_{\widetilde{i}.k}(\widetilde{t})
+%    \shortotimes -^{\widetilde{I_G}}>\longrightarrow \tau( bm(\widetilde{t}))$,
 %where $I_K = \{k/\widetilde{i}.k\in \widetilde{I_G}\uplus
@@
 %    \symb{sv}_{!\widetilde{i}}\triangleq
-%    <!um_{\widetilde{i}.k}(\widetilde{t})\otimes
+%    <!um_{\widetilde{i}.k}(\widetilde{t})\shortotimes
 %    -^{\widetilde{I_P}\uplus
-%      \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\otimes
+%      \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\shortotimes
 %    -^{\widetilde{I_G}}>\longrightarrow
@@
 %     \symb{sv}_{d(\widetilde{i}.k)}\triangleq
-%     <!dm_{\widetilde{i}.k}(\widetilde{t})\otimes
-%     -^{\widetilde{I_P}}\otimes
-%     ?m_{\widetilde{i}.k}(\widetilde{t})\otimes
+%     <!dm_{\widetilde{i}.k}(\widetilde{t})\shortotimes
+%     -^{\widetilde{I_P}}\shortotimes
+%     ?m_{\widetilde{i}.k}(\widetilde{t})\shortotimes
 %     -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}}
@@
 %     \symb{sv}_{u(\widetilde{i}.k)}\triangleq
-%     <?um_{\widetilde{i}.k}(\widetilde{t})\otimes
-%     -^{\widetilde{I_P}}\otimes
-%     !m_{\widetilde{i}.k}(\widetilde{t})\otimes
+%     <?um_{\widetilde{i}.k}(\widetilde{t})\shortotimes
+%     -^{\widetilde{I_P}}\shortotimes
+%     !m_{\widetilde{i}.k}(\widetilde{t})\shortotimes
 %     -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
@@
 %     <?m_{\widetilde{i}.k}^{\forall k\in
-%       I_K}(\widetilde{t})\otimes
-%     -^{\widetilde{I_P}}\otimes -^{\widetilde{I_G}}>\longrightarrow
+%       I_K}(\widetilde{t})\shortotimes
+%     -^{\widetilde{I_P}}\shortotimes -^{\widetilde{I_G}}>\longrightarrow
 %     ?m_{\widetilde{i}}(\widetilde{t})$,
@@
 % \item [$(DM )_{\widetilde{k}}$] $\symb{sv}_{?\widetilde{i}}\triangleq
-%     <?m_{\widetilde{i}.k}(\widetilde{t})\otimes
+%     <?m_{\widetilde{i}.k}(\widetilde{t})\shortotimes
 %     -^{\widetilde{I_P}\uplus
-%      \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\otimes -^{\widetilde{I_G}}>\longrightarrow
+%      \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\shortotimes -^{\widetilde{I_G}}>\longrightarrow
 %     ?m_{\widetilde{i}}(\widetilde{t})$,
@@
 %     <DISCARD_{\widetilde{i}.k}^{\forall k\in
-%       I_K}(\widetilde{t})\otimes
-%     -^{\widetilde{I_P}}\otimes -^{\widetilde{I_G}}>\longrightarrow
+%       I_K}(\widetilde{t})\shortotimes
+%     -^{\widetilde{I_P}}\shortotimes -^{\widetilde{I_G}}>\longrightarrow
 %     \tau(m_{\widetilde{i}.k}(\widetilde{t}))$,

### 2019-04-25 2018-Arch-pNets/Coordination Camera ready/arch-pNets.tex
Coordination revised: some improvements

@@
 \newcommand{\wrt}[1][\ ]{w.r.t.#1}
+\newcommand{\Wrt}[1][\ ]{W.r.t.#1}
 \newcommand{\resp}[1][\ ]{resp.#1}
@@
 
-%% \newcommand{\order}{\leqslant}
-\newcommand{\order}{<}
+\newcommand{\order}{\leqslant}
 \newcommand{\ordbool}{\ensuremath{\sB^{\order}}}
@@
 \newcommand{\Talg}{\ensuremath{\cT_{\signature,\variables}}}
-\newcommand{\actions}[1]{\ensuremath{\cA_{#1}}}
+\newcommand{\actions}[1]{\ensuremath{\mathit{Act}_{#1}}}
 \newcommand{\exprs}[1]{\ensuremath{\sE_{#1}}}
@@
 \newcommand{\EU}[3][\ ]{\ensuremath{\mathtt{E}\left[#2\ \mathtt{U}\ #3\right]#1}}
+\newcommand{\EW}[3][\ ]{\ensuremath{\mathtt{E}\left[#2\ \mathtt{W}\ #3\right]#1}}
 
@@
 for handling data: definition and operations on data domains, syntax
-and semantics of composition operators involving data transfer.  Under
-monotonicity assumptions on guards and assignments, composition of
+and semantics of composition operators involving data transfer.
+%
+\newCoord{We provide a property preservation result, which states that
+%
+under
+monotonicity assumptions on guards and assignments and, in presence of the \emph{maximal progress} special case of
+  priority models, additional upwards compatibility assumptions on the architectures,} composition of
 architectures preserves their characteristic safety properties.
@@
 \tuple{\{\true, \false\}, \emptyset}$ and the naturally ordered one
-$\sB^< = \tuple{\{\true, \false\}, \{\false < \true\}}$, and
+$\sB^\order = \tuple{\{\true, \false\}, \{\false \order \true\}}$, and
 similarly for integer and real numbers; as well as the set of
@@
 %can only range over given subsets of $\data$, such as $\sB$ or
-%$\sB^<$.
-%
-When speaking of an ordered sort, \eg $\sB^<$, we will assume that it
+%$\sB^\order$.
+%
+When speaking of an ordered sort, \eg $\sB^\order$, we will assume that it
 forms a meet-semilattice and denote by $\wedge$ the meet
@@
 %\item 
-$\to \subseteq S \times L \times S$ is the transition relation and 
+${\to} \subseteq S \times L \times S$ is the transition relation and 
 $L$ is the set of labels of the form
@@
        Where $s, s'\in\mathcal{S}$ and $\beta_j\in\actions{\variables}$
-        is an action of the hole $j$. $\alpha$ is the resulting global action. \Pred\ is a predicate 
+        is an action of the hole $j$; $\alpha$ is the resulting global action; {\Pred} is a predicate 
        over the different variables of the
@@
 
-\newCoord{The red dotted rule somehow expresses an implication, stating that if actions of the holes perform the designed actions and the condition is verified, then the variables are modified and the state changes.
+\newCoord{The red dotted rule expresses the implication stating that if the holes perform the designated actions and the condition $g$ is verified, then the variables are modified and the state changes.
 This implication however  uses a simple logic with the
@@
   \]
-\end{small}
+\end{small}%
 It requires the hole at label $B$ to fire a $fail(b)$ action, with the condition $b=true$ and the state variable $t<Max$.
@@
 This emits a global action $\alpha(t)$.
-\newCoord{Figure~\ref{fig:ArchFailure:OA} illustrates a whole open automaton.}
+\newCoord{Figure~\ref{fig:ArchFailure:OA} illustrates a complete open automaton.}
 %
@@
   \emph{maximal progress}.
+%
+  \newCoord{These extensions require us to define the framework in a
+    manner that would allow formulating and proving the property
+    preservation result (\thm{combining} below).  In
+    \cite{AttieBBJS16-architectures-faoc}, this result is obtained by
+    requiring, in the definition of architecture composition, that an
+    interaction among coordinated components be only possible if both
+    architectures ``agree'' that it should be enabled.  With respect
+    to data, the main difficulty lies in ensuring that this
+    ``agreement'' extends to the transferred data values.  A trivial
+    extension would allow an interaction only if the data values
+    proposed by both architectures coincide.  Considering this
+    requirement too restrictive, we go beyond by assuming the data
+    domains to be ordered and taking the \emph{meet} of the proposed
+    values.  The property preservation result then holds independently
+    of the proposed values, provided that guards and update
+    assignments are monotonic.
+
+    An important insight is that, although the requirement that guards
+    and update assignments be monotonic appears to be a limitation, it
+    is, in fact, a generalisation of the usual setting.  Indeed, the
+    usual settings, where data domains are not ordered, can be
+    recovered here by considering trivial partial orders with no two
+    distinct elements being comparable.  In such case, \emph{all
+      expressions} are trivially monotonic.
+
+    The intuition behind the proof of the preservation of safety
+    properties in \cite{AttieBBJS16-architectures-faoc} is simple.
+    The composition of two architectures combines the ``constraints''
+    that they impose on the possible executions of the system: as
+    stated above, an interaction is only enabled if both architectures
+    ``agree''.  In \cite{Baranov17-phd}, it is shown that this
+    intuition extends well to priorities in the \emph{offer semantics}
+    of BIP.  However, this is not the case in the classical semantics.
+    In this section, we informally discuss the special case of the
+    maximal progress priority models, where property preservation does
+    hold in the classical semantics of BIP.
+%
+}
 
@@
 %% $\export[\NameTimer](p) = \emptyset$, for all other ports $p$.
-Variable $t$ is implicitly assumed to be an integer.  Variables $z$
-and $\mathit{zone}$ are  integer intervals of
-the form $[l,u]$.  Both types are implicitly equipped with a
-natural ordering: increasing integers and interval inclusion.
+Variable $t$ is implicitly assumed to be \newCoord{of type Integer (with trivial ordering).  Variables $z \bydef{=} [z.l, z.u]$
+and $\mathit{zone} \bydef{=} [\mathit{zone}.l, \mathit{zone}.u]$ are   of type Integer Interval 
+ordered by interval inclusion}.
 
@@
 to the exchange of data with its environment.  However, the
-fourth premise  states that only the variables exported through the ports participating to the interaction can be affected by the data transfer.
+fourth premise  states that only the variables exported through the ports participating in the interaction can be affected by the data transfer.
 %restricts the set of
@@
   \begin{itemize}
+  \item $P_A$ and $V_A$ are sets of ports and variables, respectively;
 \item
-  $\cC$ is a finite set of \emph{coordinating components},
+  $\cC$ is a finite set of components, which we call \emph{coordinators},
   %% with pairwise disjoint sets of ports and variables,
@@
   ports in $P_A \setminus \bigcup_{C \in \cC} P_C$, which do not
-  belong to any of the coordinating components are called
+  belong to any of the coordinators are called
   \emph{dangling};
@@
 components in $\cB$.  The interface $(V_A, P_A, \export[A])$ of an
-architecture $A$ contains all ports of the coordinating
-components $\cC$ and the dangling ports, which must belong to
+architecture $A$ contains all ports of the coordinators
+$\cC$ and the dangling ports, which must belong to
 the components in $\cB$.  In the application $A(\cB)$, the ports
@@
 $\arcomp$ is associative and commutative.
-  %%; it is idempotent if all coordinating components
+  %%; it is idempotent if all coordinators
   %% are deterministic; $A_{id} = \bigl(\emptyset, \emptyset,
@@
 %% %%   Suppose we have two architectures $A \arequiv A'$.  This does not
-%% %%   necessarily mean that their sets of coordinating components
-%% %%   coincide.  However, if all the involved coordinating components
+%% %%   necessarily mean that their sets of coordinators
+%% %%   coincide.  However, if all the involved coordinators
 %% %%   are deterministic, then, in any state of $(A \arcomp A')(\cB)$,
 %% %%   both architectures will impose the same restrictions, enabling
-%% %%   the same interactions between the coordinating and operand
+%% %%   the same interactions between the coordinators and operand
 %% %%   components.  Hence, we have $(A \arcomp A')(\cB) = A(\cB) =
@@
 $\semopen{B}$ (see Definition~\ref{defn:comp:semantics}).
+
+\medskip
+\newCoord{It is well known that, since violations of safety properties
+  are characterised by finite executions, they can also be represented
+  as state predicates: intuitively, a safety property corresponds to
+  the predicate characterising the set of states, where this property
+  is not violated.}
 
@@
   additional failures having to occur in the meantime) enforced by the
-  Failure Monitor architecture can be specified using CTL as
+  Failure Monitor architecture \newCoord{comprises the safety component that} can be specified using CTL as
   %  \noteSB{Removed $\lnot \PortResume$, because not needed \emph{and} could not reformulate nicely in English.}
     $\AG
-\bigl(\PortFail \rightarrow \EX \EU[]{\lnot \PortFail}{
+\bigl(\PortFail \rightarrow \EX \EW[]{\lnot \PortFail}{
   \PortReset}\bigr)$.  Additional properties are provided in
@@
 its characteristic property on  its operand components.
-From this point of view, the set of coordinating components is
+From this point of view, the set of coordinators is
 not relevant, neither are their states.  Thus, 
@@
 interaction model $\Gamma$ respectively.
+
+\newCoord{Below, we present both the encodings of coordinators and
+  interaction models.  The key constraint is that we encode each
+  connector by one synchronisation vector.  This is necessary to
+  1)~preserve the structure of the system and 2)~allow the encoding of
+  maximal progress.
+
+  Although somewhat technical, the encoding of coordinators is, in
+  fact, pretty straightforward, comprising three key ideas: 1)~we
+  introduce an additional transition (hence also an additional state)
+  to explicitly initialise the variables; 2)~we introduce additional
+  input variables to manipulate the values provided to the coordinator
+  by the rest of the system for all exported variables; and
+  3)~following the classical technique~\cite{milner83-calculi}, we
+  simulating absence of action by an additional loop transition.
+
+  The encoding of connectors (interaction models) is more involved.
+  Since a connector represents a set of potential interactions, some
+  ports may not participate in all of them.  To encode this
+  possibility, we introduce, for each port, an additional Boolean
+  variable denoting whether the port participates in the interaction
+  or not and, for each connector, a predicate characterising the
+  interaction pattern.  Intuitively, the semantics of \emph{flat} BIP
+  connectors~\cite{BliSif08-acp-tc} depends on the synchron/trigger
+  annotations of ports.  If all ports in a connector are synchrons,
+  the only allowed interaction is that comprising all the ports, \ie
+  they all have to ``agree to interact''.  This case corresponds
+  precisely to the semantics of synchronisation vectors in pNets.  If
+  a connector has at least one trigger, then the allowed interactions
+  are those that comprise at least one trigger, \ie they must be
+  ``initiated by a trigger''.  In a hierarchical connector, these
+  principles are applied recursively.  Thus, we observe a
+  ``causality'' relation among ports of a connector: participation of
+  a synchron in an interaction \emph{implies} that of a trigger.
+  Causal Interaction Trees and Systems of Causal Rules, proposed in
+  \cite{BliSif10-causal-fmsd}, formalise this causality relation and
+  provide transformations from connectors to Boolean predicates and
+  back.  Since we use SMT techniques for the analysis of the resulting
+  pNet, the encoding presented below is optimised to reduce the number
+  of variables by treating separately the ``top-level'' triggers, \ie
+  those thereof the participation in an interaction is not subject to
+  that of any other ports.
+%
+}
 
@@
 
+\newCoord{In the following theorem, we claim an \emph{isomorphism}
+  between the open automaton semantics of a pNet encoding a BIP
+  architecture and the LTS semantics of the application of this
+  architecture to a set of simple components.  We omit the formal
+  definition of this isomorphism relation.  However, noting that open
+  automata are, essentially, symbolic representations of automata with
+  data, we can summarise it as follows: a transition belongs to the
+  LTS iff a corresponding open transition belongs to the open
+  automaton and the source and target data values of the LTS
+  transition satisfy the predicate and implement the assignments of
+  the open transition.
+%
+}
+
 \begin{theorem}
@@
 
-\add{Model-checking of open-automaton is out of the scope of this paper,
+\newCoord{Model-checking of open-automaton is out of the scope of this paper,
 though the resulting automaton here is small enough to observe the
@@
 Last, a detailed study shows that the safety property stated
-in page~\pageref{property:reset} does not hold, because of the
+on page~\pageref{property:reset} does not hold, because of the
 {\PortFail} loops on states $11$ and $12$. This is because we did not
@@
   place, c'est deja un peu long ici...}
+
 %% %****************************************************************
@@
 %% respectively.  The only exception to this cloning procedure are the
-%% sets of coordinating components: $\cC^i = \listset{\NameTimer,
+%% sets of coordinators: $\cC^i = \listset{\NameTimer,
 %%   \NameCtrl^i}$, \ie the $\NameTimer$ component is shared, while
@@
 
+\newCoord{The presented work opens a number of avenues for future
+  work, among which the most immediate ones consist in 1)~developing
+  tools that would implement the discussed encoding and verification
+  techniques and 2)~studying the preservation of liveness properties
+  by architecture composition under assumptions similar to the
+  non-interference property discussed in
+  \cite{AttieBBJS16-architectures-faoc}.}
 %The automatic checking of properties given by the pNet framework
@@
 %  
-  the projection of $\Gamma$ onto the coordinating components of
+  the projection of $\Gamma$ onto the coordinators of
   $A$.  Consider the architecture $A' = \tuple{\{C'\}, V_A, P_A, \export[A],
@@
   $g_1$, $g_2$ and $e_1$, $e_2$ are, respectively, the guards and
-  update expressions of the underlying transitions in the coordinating
-  components $C_1$ and $C_2$;
+  update expressions of the underlying transitions in the coordinators
+  $C_1$ and $C_2$;
 %    
@@
   By \lem{onlyone}, we can assume without loss of generality that each of the two
-  architectures has only one coordinating component.  For $i =
+  architectures has only one coordinator.  For $i =
   1,2$, we denote $\{C_i\} = \cC_i$, $P_i = P_{C_i}

### 2019-04-26 2018-Arch-pNets/Coordination Camera ready/arch-pNets.tex
Almost final version

@@
 \usepackage{llncsdoc}
+\usepackage[T1]{fontenc}
 
@@
 %
-\newCoord{We provide a property preservation result, which states that
-%
-under
-monotonicity assumptions on guards and assignments and, in presence of the \emph{maximal progress} special case of
-  priority models, additional upwards compatibility assumptions on the architectures,} composition of
+\newCoord{We provide a set of conditions under which} %% property preservation result holds that states that
+%% %
+%% under
+%% monotonicity assumptions on guards and assignments and, in presence of the \emph{maximal progress} special case of
+%%   priority models, additional upwards compatibility assumptions on the architectures,}
+composition of
 architectures preserves their characteristic safety properties.
@@
     extension would allow an interaction only if the data values
-    proposed by both architectures coincide.  Considering this
-    requirement too restrictive, we go beyond by assuming the data
+    proposed by both architectures coincide.  As this
+    requirement is too restrictive, we go beyond by assuming the data
     domains to be ordered and taking the \emph{meet} of the proposed
@@
   \label{defn:comp:semantics}
-  The \emph{semantics} of a component $B = \tuple{Q, q^0, V,
+  The \emph{open semantics} of a component $B = \tuple{Q, q^0, V,
   \val{0}{}, P, \export, \goesto{}}$ is %% given by
@@
 %
-  %% \todoSB{Do we actually need this?}\todoLH{I agree: I do not think we need this}
-  %% \hl{The \emph{closed semantics} of $B$ is given by the LTS denoted
-  %% $\semclosed{B} \bydef{=}\reachable{\semopen{B}}$, comprising
-  %% only the reachable states of $\semopen{B}$.}
+  The \emph{closed semantics} of $B$ is given by the LTS denoted
+  $\semclosed{B}$, comprising only those transitions of $\semopen{B}$,
+  where $\tilde{\val{}{}} = \val{}{}$, which we denote
+  $(q, \val{}{}) \goesto{a} (q', \val[\primeit]{}{})$.
 \end{definition}
@@
 %interaction.
+%
+The closed semantics excludes this possibility of data exchange.
 
@@
   \emph{priority models} that impose  a strict partial order on
-  interactions.  Formal definitions are provided in \app{arch:appendix}.  Intuitively, an interaction can be fired only if all
+  interactions.  %% Formal definitions are provided in \app{arch:appendix}.
+  Intuitively, an interaction can be fired only if all
   the higher-priority interactions available in the current state are
@@
 port $\NameTimer.\PortTick$ will never fire alone if the port $\PortFail$ is also enabled.
-In \secn{conclusion}, we discuss the generalisation of the
-obtained results to other priority models.
+%% In \secn{conclusion}, we discuss the generalisation of the
+%% obtained results to other priority models.
 
@@
 %\label{secn:safety}
-For a component $B$, we denote $S_{\semopen{B}}$ and
-$s^0_{\semopen{B}}$ the corresponding constituents of
-$\semopen{B}$ (see Definition~\ref{defn:comp:semantics}).
 
@@
 
+For a component $B$, we denote $S_{\semclosed{B}}$ and
+$s^0_{\semclosed{B}}$ the corresponding constituents of
+$\semclosed{B}$ (see Definition~\ref{defn:comp:semantics}).
+
 \begin{definition}[Properties]
@@
   of $B$ is a predicate $\Phi$ on
-  $S_{\semopen{B}}$, such that $\bigl((q,
+  $S_{\semclosed{B}}$, such that $\bigl((q,
   \val{}{}) \models \Phi\bigr) \land (\val[\primeit]{}{} \order
@@
   A property $\Phi$ is \emph{initial} if
-  $s^0_{\semopen{B}} \models \Phi$.
+  $s^0_{\semclosed{B}} \models \Phi$.
   %% \todoSB{Do we need this?}\hl{;
   %% it is \emph{reachable} iff there exists a possibly empty path
-  %% $s^0_{\semopen{B}} \goesto{a^1, \val{1}{}} s^1 \goesto{a^2,
+  %% $s^0_{\semclosed{B}} \goesto{a^1, \val{1}{}} s^1 \goesto{a^2,
   %%   \val{2}{}} \cdots \goesto{a^n, \val{n}{}} s^n$, such that
@@
 \bigl(\PortFail \rightarrow \EX \EW[]{\lnot \PortFail}{
-  \PortReset}\bigr)$.  Additional properties are provided in
-\app{properties}.
+  \PortReset}\bigr)$.  %% Additional properties are provided in
+%% \app{properties}.
 %% \todoSB{Cite the original paper somewhere.}
@@
     $\cB$} iff, for every state $s = (s_c, s_b)$ reachable in
-  $\semopen{A(\cB)}$, with 
-  $s_c \in \prod_{C \in \cC} S_{\semopen{C}}$ and
-  $s_b \in \prod_{B \in \cB} S_{\semopen{B}}$,
+  $\semclosed{A(\cB)}$, with 
+  $s_c \in \prod_{C \in \cC} S_{\semclosed{C}}$ and
+  $s_b \in \prod_{B \in \cB} S_{\semclosed{B}}$,
   we have $s_b \models \Phi$.
@@
 %Below, we omit mentioning this explicitly.
-\defn{up:compat} in \app{arch:appendix} formally defines
+In \cite{arch-pNets-RR}, we formally define
  \emph{upwards compatibility} that ensures property preservation when composing architectures. Informally, two architectures $A_1$ and $A_2$
@@
   3)~following the classical technique~\cite{milner83-calculi}, we
-  simulating absence of action by an additional loop transition.
+  simulate the absence of action by an additional loop transition.
 
@@
   pNet, the encoding presented below is optimised to reduce the number
-  of variables by treating separately the ``top-level'' triggers, \ie
-  those thereof the participation in an interaction is not subject to
-  that of any other ports.
+  of variables by treating separately the ``top-level'' triggers (\eg
+  $\NameTimer.\PortTick$ in the connector {\NameTimer.\PortTick
+    \trigsynch (\PortFail \trigsynch \NameCtrl.\PortFail)} in
+  \fig{schema:ArchFailure:BIP}).
 %
@@
 causal rules, which are Boolean implications similar to the ones in
-the example above.  We briefly summarise the key definitions and
-results in \app{algebras}.  The $\ac(P)$, $\ct(P)$ and $\cru(P)$
+the example above.  %% We briefly summarise the key definitions and
+%% results in \app{algebras}.
+The $\ac(P)$, $\ct(P)$ and $\cru(P)$
 representations of the connectors in \fig{schema:ArchFailure:BIP} are
@@
 \begin{table}[t]
-  \caption{Algebraic representations of the connectors in \fig{schema:ArchFailure:BIP} (see \app{algebras})}
+  \caption{Algebraic representations of the connectors in \fig{schema:ArchFailure:BIP}}
   \label{tab:connectors}
@@
 \ac(P_A) \rightarrow \ct(P_A)$ and $R : \ct(P_A) \rightarrow
-\cru(P_A)$ the two mappings defined in \app{transformations} and
+\cru(P_A)$ the two mappings \cite{BliSif10-causal-fmsd} discussed above and
 illustrated in \tab{connectors}, $\bigl[\nicefrac{b_p}{p}\bigr]$ is
@@
 most one action of interest (see the properties in
-\app{properties}).
+\cite{arch-pNets-RR}).
 %% In the general encoding, the global actions of the
@@
   between the open automaton semantics of a pNet encoding a BIP
-  architecture and the LTS semantics of the application of this
-  architecture to a set of simple components.  We omit the formal
-  definition of this isomorphism relation.  However, noting that open
-  automata are, essentially, symbolic representations of automata with
-  data, we can summarise it as follows: a transition belongs to the
-  LTS iff a corresponding open transition belongs to the open
-  automaton and the source and target data values of the LTS
-  transition satisfy the predicate and implement the assignments of
-  the open transition.
+  architecture and the LTS semantics of this architecture applied to a
+  set of simple components.  We omit the formal definition of this
+  isomorphism relation.  However, noting that open automata are,
+  essentially, symbolic representations of automata with data, we can
+  summarise it as follows: a transition belongs to the LTS iff a
+  corresponding open transition belongs to the open automaton and the
+  source and target data values of the LTS transition satisfy the
+  predicate and implement the assignments of the open transition.
 %
@@
   $\nopri[A,\partition]$ is
-  isomorphic to the LTS $\semopen{\Gamma\bigl(\cC_A, (B_D)^{D \in
+  isomorphic to the LTS $\semclosed{\Gamma\bigl(\cC_A, (B_D)^{D \in
       \partition}\bigr)}$ (see \defn{comp:semantics}), with, for each
@@
 In the SV guard, we have to check whether \emph{all ports
-  leading to $p$ in the causal tree $\tau(x)$ can be fired} (see
-\app{transformations}).  If so, then $p$ must be fired, \ie
+  leading to $p$ in the causal interaction tree $\tau(x)$ can be fired} (see the second column of
+\tab{connectors} for examples).  If so, then $p$ must be fired, \ie
 $p(\false)$ must be blocked.
@@
 action; full details can be found in 
-\app{full-results}.
+\cite{arch-pNets-RR}.
 %
@@
 This automaton has 12 transitions, including those encoding various
-possible firing of some interactions (e.g. OT 2 and 3 for
-{\PortFail}).
+possible firing of some interactions, \eg $OT_2$ and $OT_3$ for
+{\PortFail}.
+\newCoord{Notice, however, that the global actions of these open transitions have an additional Boolean parameter.
+In this context, model checking should be understood after application of the encoding, namely here the original {\PortFail} event must be an effective ``fail'' of the hole ``B'', that is a $\mathit{fail}(\mathit{true})$ action in the open automaton.}
 
@@
 on page~\pageref{property:reset} does not hold, because of the
-{\PortFail} loops on states $11$ and $12$. This is because we did not
+{\PortFail} loop on state $11$.  This is because we did not
 use the maximal progress assumption here.  If we do, we get the
-corrected behaviour in \fig{ArchFailure:OA-MaxProgress}
-(\app{full-results}), in which $OT_7$ has disappeared, and $OT_2$ and
-$OT_{10}$ have been restricted to $b0=\false$. This one verifies all
-the properties listed in \app{properties}.
-
-\noteEMin{on peut encore bouger deux lignes de l'annexe D.2, pour
-  mentionner ici une propriete de liveness, mais ca va dependre de la
-  place, c'est deja un peu long ici...}
+corrected behaviour %% in \fig{ArchFailure:OA-MaxProgress}
+%% (\app{full-results}), in which
+where
+$OT_7$ disappears, and $OT_2$ and
+$OT_{10}$ are restricted to $b0=\false$. This one verifies all
+the properties listed above.%% in \app{properties}.
+
+%% \noteEMin{on peut encore bouger deux lignes de l'annexe D.2, pour
+%%   mentionner ici une propriete de liveness, mais ca va dependre de la
+%%   place, c'est deja un peu long ici...}
 
@@
   tools that would implement the discussed encoding and verification
-  techniques and 2)~studying the preservation of liveness properties
-  by architecture composition under assumptions similar to the
-  non-interference property discussed in
-  \cite{AttieBBJS16-architectures-faoc}.}
+  techniques; 2)~studying the preservation of liveness properties by
+  architecture composition under assumptions similar to those
+  discussed in \cite{AttieBBJS16-architectures-faoc} and
+  3)~generalisation to priority models other than maximal progress.}
 %The automatic checking of properties given by the pNet framework
@@
 %****************************************************************
+\end{document}
+
 \appendix

### 2019-04-26 2018-Arch-pNets/Coordination Camera ready/arch-pNets.tex
arch-pNets paper: run a spell-checker

@@
 connectors.  The causal semantics of the connectors, given in terms of
-the Algebra of Causal Interaction Trees $\ct(P)$, explicitates the
+the Algebra of Causal Interaction Trees $\ct(P)$, elicits the
 causal dependencies through an encoding mapping

### 2019-04-26 2018-Arch-pNets/Coordination Camera ready/arch-pNets.tex
arch-pNets paper: Final camera-ready version to be submitted

@@
   \setTupleDelims[\mylangle]{\myrangle}%
+  \tuplebase[#1]{#2}%
+}
+
+\newcommand{\SVTuple}[2][\ensuremath{,\allowbreak}]{%
+  \setTupleDelims[\langle]{\rangle}%
   \tuplebase[#1]{#2}%
@@
 %For a valuation $\val{}{}$ and an assignment $(x_i := e_i)^{i \in I}$, we define:
-\vspace{-1.5ex}
+%% \vspace{-1.5ex}
 \[
@@
   \val{}{}(e_i), & \text{if } x = x_i, \text{for some } i \in I\,.
-\end{cases}\vspace{-1ex}
+\end{cases}%% \vspace{-1ex}
 \]
@@
 Variables of each state are pairwise disjoint.
-\newCoord{The parameters of actions that appear on pLTS transitions are either input variables, bound when the action occurs and accepting any value (of the right type), or expressions using the value of other variables.}
+\newCoord{Each transition label of a pLTS consists of a parameterised action, a guard and an update assignment.
+The parameters of actions are either input variables or expressions.
+Input variables are bound when the action occurs; they accept any value (of the correct type), thus providing a to input data from the environment.
+Expressions are computed from the values of other variables.
+They allow providing aggregated values to the environment, without exposing all the underlying variables.}
 We  define the set of parameterised actions a pLTS can use ($a$
@@
  Proposition and inference rules of the paper use a standard logic, while predicates inside the open transitions should use a more restricted logic, typically a logic that could  be handled mechanically and expressed by terms that can be encoded in a simple syntax.
-Open transitions express in a symbolic way, transitions  that are not only parametrised with variables but also actions of not yet known processes.}
+Open transitions express in a symbolic way, transitions  that are not only parameterised with variables but also actions of not yet known processes.}
 
@@
 
-\begin{example}[An open-transition]
-  \label{ex:TimerOT3}
-We now briefly illustrate an open transition:
-\begin{small}\[ \openrule
-  {\{B\mapsto fail(b)\},
-    t<Max \land b=true ,
-    \{t' := t+1\} }
-  {\ostate{11} \OTarrow{\alpha(t)} \ostate{14}}\vspace{-1.3ex}
+\begin{example}[An open transition]
+  \label{ex:TimerOT5}
+  \newCoord{The open transition
+  \begin{small}
+    \[
+    \openrule{
+      \{E\mapsto ask\},
+      t \in z,
+      \{t:=t+1\}
+    }{
+      \ostate{11} \OTarrow{ask} \ostate{11}
+    }
     \]
   \end{small}%
-It requires the hole at label $B$ to fire a $fail(b)$ action, with the condition $b=true$ and the state variable $t<Max$.
-In this case, the global pNet goes from state $\ostate{11}$ that has an internal variable $t$ to state $\ostate{14}$ where the state variable $t'$ has the value $t+1$.
-This emits a global action $\alpha(t)$.
-\newCoord{Figure~\ref{fig:ArchFailure:OA} illustrates a complete open automaton.}
+%% \begin{small}\[ \openrule
+%%   {\{B\mapsto \mathit{fail}(b)\},
+%%     t<Max \land b=true ,
+%%     \{t := t+1\} }
+%%   {\ostate{11} \OTarrow{\alpha(t)} \ostate{14}}%% \vspace{-1.3ex}
+%%   \]
+%% \end{small}
+%
+emits a global action $ask$ labelling the synchronisation vector $\SVTuple{\mathit{timeout}_T, \mathit{timeout}_C, -, \mathit{ask}} \rightarrow \mathit{ask}$.
+It requires the hole at label $E$ to fire an $\mathit{ask}$ action, with the condition $t \in z$.
+In this case, the global pNet loops on the state $\ostate{11}$ that has internal variables $t$ and $z$ local to the pLTS $T$ (hence not appearing in the synchronisation vector).
+The variable $t$ is updated to the new value $t+1$.
+\Fig{FailureTimer:pNet} shows the complete pNet, whereas \fig{ArchFailure:OA} shows a complete open automaton.}
 %
@@
   A component is a tuple $\tuple{Q, q^0, V, \val{0}{}, P,
-  \export, \goesto{}}$ where\vspace{-2ex}
+  \export, \goesto{}}$ where%% \vspace{-2ex}
   \begin{itemize}
@@
 %
+  \newCoord{%
     The \emph{closed semantics} of $B$ is given by the LTS denoted
   $\semclosed{B}$, comprising only those transitions of $\semopen{B}$,
-  where $\tilde{\val{}{}} = \val{}{}$, which we denote
-  $(q, \val{}{}) \goesto{a} (q', \val[\primeit]{}{})$.
+  where $\tilde{\val{}{}} = \val{}{}$.}%% , which we denote
+  %% $(q, \val{}{}) \goesto{a} (q', \val[\primeit]{}{})$.}
 \end{definition}
@@
   An \emph{architecture} is a tuple $A = \tuple{\cC, V_A, P_A,
-    \export[A], \Gamma}$, where\vspace{-1.5ex}
+    \export[A], \Gamma}$, where%% \vspace{-1.5ex}
   \begin{itemize}
@@
   $A_2$ is the architecture $A_1 \arcomp A_2 = \tuple{\cC_1 \cup \cC_2,
-  V_{A_1} \cup V_{A_2}, P_{A_1} \cup P_{A_2}, \export[A_1] \cup \export[A_2], \Gamma}$, where\vspace{-1ex}
+  V_{A_1} \cup V_{A_2}, P_{A_1} \cup P_{A_2}, \export[A_1] \cup \export[A_2], \Gamma}$, where%% \vspace{-1ex}
 %
@@
 %% Aside from previous work on pNets and BIP architectures mentioned in \secn{introduction}.
-We  review here the closest related works outside the scope of pNets and BIP architectures, with a particular focus on compositional and parameterized verification.
+We  review here the closest related works outside the scope of pNets and BIP architectures, with a particular focus on compositional and parameterised verification.
 
@@
 
-%% infinite/parametrized model checking? == ERIC (listes ci-dessous)  + Simon
+%% infinite/parameterised model checking? == ERIC (listes ci-dessous)  + Simon
 

### 2019-04-26 2018-Arch-pNets/Coordination sources/arch-pNets.tex
arch-pNets paper: Prepared the sources for submission -- removed all 'Overfull's

--- 2019-04-26 2018-Arch-pNets/Coordination Camera ready/arch-pNets.tex
@@
 	\label{defn:open-automaton}
-	An \emph{open automaton} is a tuple $<\!\!J,\mathcal{S},s_0,\mathcal{T}\!\!>$ where:
+	An \emph{open automaton} is a tuple $(J,\mathcal{S},s_0,\mathcal{T})$ where:
 %	\begin{itemize}
@@
 %
-emits a global action $ask$ labelling the synchronisation vector $\SVTuple{\mathit{timeout}_T, \mathit{timeout}_C, -, \mathit{ask}} \rightarrow \mathit{ask}$.
+emits a global action $ask$ defined by the synchronisation vector $\SVTuple{\mathit{timeout}_T, \mathit{timeout}_C, -, \mathit{ask}} \rightarrow \mathit{ask}$.
 It requires the hole at label $E$ to fire an $\mathit{ask}$ action, with the condition $t \in z$.
@@
   A component is a tuple $\tuple{Q, q^0, V, \val{0}{}, P,
-  \export, \goesto{}}$ where%% \vspace{-2ex}
+  \export, \goesto{}}$, where%% \vspace{-2ex}
   \begin{itemize}
@@
     \infer{    
+      \forall i \in \supp{a}, q_i \goesto{a \cap P_i, g_i, u_i} q_i'
+      \and
+      \forall i \not\in \supp{a}, q_i = q_i'
+%
+      \\\\
+      \textstyle
+%
+      g' = g \land \bigwedge_{i \in \supp{a}} g_i
+      \and
+      u' = u; u_i^{i \in \supp{a}}
+      \and
       (a, g, u) \in \Gamma
@@
       a \neq \emptyset
-      \and
-      \forall i \in \supp{a}, q_i \goesto{a \cap P_i, g_i, u_i} q_i'
-      \and
-      \forall i \not\in \supp{a}, q_i = q_i'
-%
-      \\\\
-      \textstyle
-%
-      g' = g \land \bigwedge_{i \in \supp{a}} g_i
-      \and
-      u' = u; u_i^{i \in \supp{a}}
     }{
@@
 \item
-  $\cC$ is a finite set of components, which we call \emph{coordinators},
+  $\cC$ is a finite set of components (called \emph{coordinators}),
   %% with pairwise disjoint sets of ports and variables,
@@
 \end{document}
-
-\appendix
-\clearpage
-
-\noindent
-%\add{
-The following appendices are included for convenience and would be integrated into a research report if the paper is accepted for publication.
-The first appendix provides previously published complementary information, whereas the subsequent ones give additional formal details complementing architecture definitions, proofs of theorems, and the case study.
-%}
-
-\section{Algebraic representations of the interaction model}
-\label{secn:algebras}
-
-This section presents some material that has already been published in earlier work but is essential for understanding the encoding in \secn{encoding}.
-It is condensed from
-\cite[Section~4]{BarBliu15-offer-scico} and recalls briefly the syntax
-and semantics of the algebras used to represent BIP interaction models
-\emph{disregarding variables and data transfer}.
-
-All the algebras are
-parameterised by a set $P$ of all the ports in a given system.  The
-semantics of the Algebra of Interactions $\ai(P)$ is given in terms of
-sets of interactions by a function $\intsem{\cdot}: \ai(P) \rightarrow
-2^{2^P}$.  The corresponding equivalence relation on $\ai(P)$ is
-defined as follows: two terms $x,y \in \ai(P)$ are {\em equivalent} $x
-\simeq y$ iff $\intsem{x} = \intsem{y}$.  For any other algebra
-$\cA(P)$ among those appearing in this section, we define its
-semantics by the function $\aisem{\cdot}: \cA(P) \rightarrow \ai(P)$.
-A function $\intsem{\cdot}: \cA(P) \rightarrow 2^{2^P}$ is obtained by
-composing $\aisem{\cdot}: \cA(P) \rightarrow \ai(P)$ and
-$\intsem{\cdot}: \ai(P) \rightarrow 2^{2^P}$.  The axiomatisation of
-$\ai(P)$ given in \cite{BliSif07-acp-emsoft} is sound and complete
-with respect to $\simeq$.  Hence, for other algebras, the equivalences
-induced by $\intsem{\cdot}$ and $\aisem{\cdot}$ coincide.
-
-Below, we assume that a set of ports $P$ is given, such that $0,1\not\in
-P$.
-
-For any set $X$ of propositional variables, we denote by $\sB[X]$ the
-corresponding Boolean algebra generated by $X$.  For presentation
-clarity, we will often omit the conjunction operator and write $a \lor
-bc$ instead of $a \lor (b \land c)$.
-
-% *********************************************************************
-
-\subsection{Algebra of Interactions}
-\label{secn:ai}
-
-The Algebra of Interactions is used to define the interaction semantics of other algebras. The elements of this algebra can be bijectively mapped to interaction models, \ie subsets of $2^P$.
-
-\begin{syntax}
-The syntax of the {\em Algebra of Interactions}, $\ai(P)$, is defined by
-the following grammar
-%
-\begin{equation} \label{eq:apsynt}
-  \begin{array}{rc*{4}{l@{\ |\ }}l}
-    x & ::= & 0 & 1 & p \in P & x\cdot x & x + x \,,\\
-  \end{array}
-\end{equation}
-%
-where `$+$' and `$\cdot$' are binary operators, respectively called
-{\em union} and {\em synchronisation}.  Synchronisation binds stronger
-than union.
-\end{syntax}
-%
-As follows from the interaction semantics given below, the additive
-identity element $0$ represents blocking, since it does not authorise
-any interaction.  The multiplicative identity element $1$ corresponds
-to the empty interaction, which represents idling (see the discussion
-in \cite{BarBliu15-offer-scico}).
-
-\begin{semantics}
-The semantics of $\ai(P)$ is given by the function $\|\cdot\| : \ai(P)
-\rightarrow 2^{2^P}$, defined by
-%
-\begin{equation} \label{eq:apsem}
-  \renewcommand{\arraystretch}{1.5}
-  \begin{array}{lcl}
-    \lefteqn{\|0\|\ =\ \emptyset,\quad \|1\|\ =\ \{\emptyset\},\quad
-      \|p\|\ =\ \Big\{\{p\}\Big\},}\\
-    \|x_1 + x_2\| &=& \|x_1\| \cup \|x_2\|,\\
-    \|x_1 \cdot x_2\| &=& 
-    \Big\{a_1 \cup a_2\,\Big|\, a_1\in \|x_1\|, a_2\in \|x_2\| \Big\},
-  \end{array}
-\end{equation}
-for $p\in P$, $x_1,x_2\in\ai(P)$.  Terms of $\ai(P)$ represent sets of
-interactions between the ports $P$.
-\end{semantics}
-
-A sound and complete axiomatisation of $\ai(P)$ with respect to the
-semantic equivalence is provided in \cite{BliSif07-acp-emsoft}.  In a
-nutshell, $(\ai(P), +, \cdot, 0, 1)$ is a commutative semiring,
-idempotent in both $+$ and $\cdot$.
-
-% *********************************************************************
-
-\subsection{Algebra of Connectors}
-\label{secn:ac}
-
-The Algebra of Connectors provides an algebraic formalisation for
-structuring the interaction models.  It underlies the graphical
-notation (\eg \fig{connectors}) and the syntax for connectors used in the BIP language.
-
-\begin{syntax}
-The syntax of the {\em Algebra of Connectors}, $\ac(P)$, is defined by the
-following grammar
-%
-\begin{equation} \label{eq:acsynt}
-  \renewcommand{\arraystretch}{1.5}
-  \begin{array}{lcll}
-    s & ::= & [0]\ |\ [1]\ |\ [p]\ |\ [x] \:\:\:\:\:\:\:\:\:(synchrons)\\
-    t & ::= & [0]'\ |\ [1]'\ |\ [p]'\ |\ [x]'  \:\:\:\:\:\:   (triggers)\\
-    x & ::= & s\ |\ t\ |\ x\cdot x\ |\ x + x\,, 
-  \end{array}
-\end{equation}
-for $p\in P$, and where `$+$' is a binary operator called {\em union},
-`$\cdot$' is a binary operator called {\em fusion}, and brackets
-`$[\cdot]$' and `$[\cdot]'$' are unary {\em typing} operators.  Fusion
-binds stronger than union.
-
-Union has the same meaning as union in $\ai(P)$. Fusion is a
-generalisation of the synchronisation in $\ai(P)$.  Typing is used to
-form typed connectors: `$[\cdot]$' defines {\em synchrons} (need
-synchronisation with other ports in order to interact) and
-`$[\cdot]'$' defines {\em triggers} (can initiate an interaction).
-\end{syntax}
-
-In order to simplify notation, we will omit brackets on 0, 1, and
-ports $p \in P$, as well as `$\cdot$' for the fusion operation.
-
-\begin{definition}
- In a system with a set of ports $P$, connectors are elements of $\ac(P)$.
-\end{definition}
-
-The operations of the Algebra of Connectors satisfy the following
-axioms.
-\begin{itemize}
-\item Union `$+$' is associative, commutative, idempotent and has the identity element 0.
-\item Fusion `$\cdot$' is associative, commutative and has the identity element 1.
-It is idempotent on monomial connectors, \ie[,] for any $x \in \ac(P)$, not involving the union operation, we have $x\cdot x = x$.
-\item Typing `$[\cdot]^*$' satisfies the following axioms, for $x,y,z
-  \in \ac(P)$ and $[\cdot]^\alpha,[\cdot]^\beta \in \bigl\{[\cdot]', [\cdot]\bigr\}$ arbitrary typings (trigger or synchron):
-  \begin{enumerate}
-  \item $[0] = [0]'$,
-  \item $[[x]^\alpha]^\beta = [x]^\beta$,
-  \item $[x + y]^\alpha = [x]^\alpha + [y]^\alpha$,
-  \item $[x]'[y]' = [x]'[y] + [x][y]'$.
-  \end{enumerate}
-\end{itemize}
-Complete axiomatisation of $\ac(P)$ with respect to the semantic
-equivalence is provided in \cite{BliSif08-acp-tc}.
-
-\begin{semantics}
-The semantics of $\ac(P)$ is given by the function $|\cdot| : \ac(P)
-\rightarrow \ai(P)$ (we use the $\sum$ and $\prod$ notation for,
-respectively, the union and fusion of multiple terms of $\ac(P)$):
-%
-\begin{align}
-  \label{eq:acap}
-  |[p]| & = p\,,
-  & |x_1 + x_2| & = |x_1| + |x_2|\,,x
-  & \left|\prod_{i=1}^n [x_i]\,\right| & = \prod_{i=1}^n |x_k|\,,
-  \\
-  \label{eq:acaptrig}
-  && \hspace{-2cm}\left|\prod_{i=1}^n [x_i]' \prod_{j=1}^m [y_j]\,\right| = 
-  \sum_{i=1}^n |x_i| & \lefteqn{\left(
-  \prod_{k\not=i}\Big(1 + |x_k|\Big)\ \prod_{j=1}^m \Big(1 + |y_j|\Big)\right)}\,
-\end{align}
-%
-for $n > 0$, $m \geq 0$, $x_1,\dots,x_n,y_1,\dots,y_m \in \ac(P)$ and
-$p\in P\cup \{0,1\}$.
-\end{semantics}
-
-\fig{connectors} shows four basic examples of the graphical
-representation of connectors.  Triggers are denoted by triangles,
-whereas synchrons are denoted by bullets.  The interaction semantics
-of the four connectors is given in the sub-figure captions.
-
-\begin{figure}[t]
-  \centering
-  \begin{subfigure}[b]{0.18\textwidth}
-    %% \rule{\textwidth}{0.5pt}
-    \centering
-    \input{figures/rdv.pspdftex}
-    \caption{\centering Rendezvous~$pqr$
-      $\intsem{pqr} = \{pqr\}$}
-    \label{fig:connectors:rdv}
-  \end{subfigure}%
-  \hfill %add desired spacing between images, e. g. ~, \quad, \qquad etc.
-  %(or a blank line to force the subfigure onto a new line)
-  \begin{subfigure}[b]{0.24\textwidth}
-    %% \rule{\textwidth}{0.5pt}
-    \centering
-    \input{figures/broadcast.pspdftex}
-    \caption{\centering Broadcast~$p'qr$
-      $\intsem{p'qr} = \{p, pq, pr, pqr\}$}
-    \label{fig:connectors:bdc}
-  \end{subfigure}%
-  \hfill %add desired spacing between images, e. g. ~, \quad, \qquad etc.
-  %(or a blank line to force the subfigure onto a new line)
-  \begin{subfigure}[b]{0.24\textwidth}
-    %% \rule{\textwidth}{0.5pt}
-    \centering
-    \input{figures/atomic-bdc.pspdftex}
-    \caption{\centering Atomic broadcast~$p'[qr]$
-      $\intsem{p'[qr]} = \{p, pqr\}$}
-    \label{fig:connectors:atomic}
-  \end{subfigure}%
-  \hfill %add desired spacing between images, e. g. ~, \quad, \qquad etc.
-  %(or a blank line to force the subfigure onto a new line)
-  \begin{subfigure}[b]{0.23\textwidth}
-    %% \rule{\textwidth}{0.5pt}
-    \centering
-    \input{figures/causal-chain.pspdftex}
-    \caption{\centering Causal chain~$p'[q'r]$
-      $\intsem{p'[q'r]} = \{p, pq, pqr\}$}
-    \label{fig:connectors:causal}
-  \end{subfigure}%
-  \caption{Basic connector examples}
-  \label{fig:connectors}
-\end{figure}
-
-The semantic equivalence $\simeq$ is not a congruence for $\ac(P)$.
-We denote by $\cong$ the largest congruence relation contained in
-$\simeq$.
-
-\begin{property}[\cite{BliSif08-acp-tc}]
-  \label{prop:cong}
-  For any $x, y \in \ac(P)$, we have $[x]'[y]' \cong \bigl[[x]'[y]'\bigr]'$.
-\end{property}
-
-%*********************************************************************
-
-\subsection{Algebra of Causal Interaction Trees}
-\label{secn:trees}
-
-The Algebra of Causal Interaction Trees serves as a pivot for
-transformations between all other algebraic representations.  It makes
-explicit the causal dependencies between ports contributing to the
-interactions defined by a connector.
-
-\begin{syntax}
-The syntax of the \emph{Algebra of Causal Interaction Trees}, $\ct(P)$, is
-given by
-\begin{equation} \label{eq:ctsyn}
-  t ::= a \,|\, a \rightarrow t \,|\, t\oplus t\,,
-\end{equation}
-where $a \in \ai(P)$ is an interaction, \ie $0$, $1$ or a
-synchronisation of ports (without the use of the union operator), and
-`$\rightarrow$' and `$\oplus$' are respectively the {\em causality}
-and the {\em parallel composition} operators.  Causality binds
-stronger than parallel composition.  Notice that a causal interaction
-tree can have several roots.
-\end{syntax}
-
-``Atomic'' strongly synchronised interactions in the nodes of a causal
-interaction tree are the building blocks for the interactions provided
-by the connector.  The causality operator defines a dependency between
-two interactions: $a \rightarrow b$ means that for $b$ to
-participate in the overall interaction, $a$ must also participate.
-The parallel composition allows one to combine interactions without
-introducing dependencies: any combination of $a$
-and $b$ can participate in $a \oplus b$.
-
-The causality operator is right- (but not left-) associative: for
-interactions $a_1,\dots,a_n$, we have $a_1 \rightarrow (a_2
-\rightarrow (\dots \rightarrow a_n)\dots)) = a_1 \rightarrow a_2
-\rightarrow \dots \rightarrow a_n$.  We call this construction a {\em
-  causal chain}.
-
-\begin{semantics}
-The semantics of $\ct(P)$ is given by the function $|\cdot|: \ct(P)
-\rightarrow \ai(P)$
-\begin{align}
-  \label{eq:ctsem}
-  |a| & = a\,,
-  & |a \rightarrow t| & = a\Big(1 + |t|\Big)\,,
-  & |t_1 \oplus t_2| & = |t_1| + |t_2| + |t_1|\,|t_2|\,,
-\end{align}
-where $a\in 2^P \cup \{0,1\}$ is an interaction and $t, t_1, t_2 \in \ct(P)$.
-\end{semantics}
-
-A sound axiomatisation of $\ct(P)$ is provided in
-\cite{BliSif10-causal-fmsd}.
-
-% *********************************************************************
-
-\subsection{Systems of Causal Rules}
-\label{secn:rules}
-
-Systems of causal rules represent an intermediate structure between
-causal interaction trees and arbitrary Boolean formulas.  They
-directly encode the causality information explicit in the causal
-interaction trees, by transforming causality relations into dual Horn
-clauses. %%  Apart from supporting connector synthesis, they provide a
-%% convenient way for expressing properties to be enforced by the glue
-%% operators (see \secn{example} for some examples).  Causal rules
-%% have also served as basis for the macro-notation used to specify
-%% the glue in Dy-BIP\mdash a dynamic flavour of BIP \cite{dybip}.
-
-\begin{definition}
-  A {\em causal rule} is a Boolean formula in $\sB[P]$ of the form $E
-  \Rightarrow C$.  The \emph{effect} $E$ is either the constant
-  $\true$ or a port variable $p \in P$.  The \emph{cause} $C$ is
-  either a constant, $\true$ or $\false$, or a disjunction of
-  interactions, \ie $\bigvee_{i=1}^n a_i$ where, for all $i\in [1,n]$,
-  $a_i$ are conjunctions of positive port variables.
-\end{definition}
-
-\begin{note} \label{rem:absorption}
-  Notice that $a_1 \lor a_1\,a_2 = a_1$, and therefore causal rules
-  can be simplified by replacing $p \Rightarrow a_1 \lor a_1\,a_2$
-  with $p \Rightarrow a_1)$.  We assume that all the causal rules are
-  simplified by this absorption rule.
-\end{note}
-
-\begin{definition}
-  A \emph{system of causal rules} is a set $R = \{p \Rightarrow
-  x_p\}_{p\in P\cup \{\true\}}$.  An interaction $a \in 2^P$ satisfies
-  the system $R$ (denoted $a \models R$), iff the characteristic
-  valuation of $a$ on $P$ satisfies the formula $\bigwedge_{p\in P\cup
-    \{\true\}} (p \Rightarrow x_p)$.  We denote by
-  $|R|\ \bydef{=}\ \sum_{a \models R} a$ the union (in terms of the
-  Algebra of Interactions) of the interactions satisfying $R$.  Thus
-  we have $|\cdot| : \cru(P) \rightarrow \ai(P)$, where $\cru(P)$ is
-  the set of all systems of causal rules over the set of port
-  variables $P$.
-\end{definition}
-
-%*********************************************************************
-
-\subsection{Transformations between algebraic representations of interaction models}
-\label{secn:transformations}
-
-Transformations $\ac(P)
-\overset{\tau}{\underset{\sigma}{\rightleftarrows}} \ct(P)$, $\ct(P)
-\overset{R}{\rightleftarrows} \cru(P)$ and $\cru(P) \rightleftarrows
-\sB[P]$ were defined in \cite{BliSif10-causal-fmsd} and have been
-shown to respect $\simeq$.  Below, we recall only the transformations
-that are used in this paper.
-
-We define the function $\tau : \ac(P) \rightarrow \ct(P)$, associating
-a causal interaction tree with a connector.  By \prop{cong}, and the
-associativity of both fusion in $\ac(P)$ and parallel composition in
-$\ct(P)$, the following equations are sufficient to define $\tau$:
-%
-\begin{align}
-  \label{eq:contree:p}
-  \tau(p) &= p
-  \,,\\
-  \label{eq:contree:trigsynch}
-  \tau\left(
-  [x]'\prod_{i=1}^n [y_i]
-  \right) &=
-  \tau(x) \rightarrow \bigoplus_{i=1}^n \tau(y_i)
-  \,,\\
-  \label{eq:contree:trig}
-  \tau\bigl([x_1]'[x_2]'\bigr) &= \tau(x_1) \oplus \tau(x_2)
-  \,,\\
-  \label{eq:contree:sync}  
-  \tau\bigl([y_1][y_2]\bigr) &=
-  \bigoplus_{i = 1}^{m_1}\bigoplus_{j = 1}^{m_2} a_i^1 a_j^2
-  \rightarrow (t_i^1 \oplus t_j^2)
-  \,,
-\end{align}
-%
-where $x, x_1, x_2, y_1,\dots, y_n \in \ac(P)$, $p \in P \cup \{0,1\}$
-and, in \eq{contree:sync}, we assume $\tau(y_k) = \bigoplus_{i =
-  1}^{m_k} a_i^k \rightarrow t_i^k$, for $k = 1,2$.
-
-%% $\sigma : \ct(P) \rightarrow \ac(P)$ is defined recursively by putting
-%% %
-%% \begin{align}
-%%   \label{eq:treecon}
-%%   \sigma(a) & = [a]\,,
-%%   & \sigma(a \rightarrow t) & = [a]'\,[\sigma(t)]\,,
-%%   & \sigma(t_1 \oplus t_2)  & = [\sigma(t_1)]'\,[\sigma(t_2)]'\,.
-%% \end{align}
-
-We define $R: \ct(P) \rightarrow \cru(P)$ by putting
-%
-\begin{equation} 
-  \label{eq:trees2rules}
-  R(t)\ =\ \{p \Rightarrow c_p(t)\}_{p\in P\cup\{\true\}}\,,
-\end{equation}
-where the function $c_p : \ct(P) \rightarrow \sB[P]$ is defined recursively
-as follows.  For $a\in 2^P$ (with $p\not\in a$) and $t,t_1,t_2 \in \ct(P)$,
-we put
-%
-\begin{align*}
-  c_p(0) & = \false\,, 
-  & c_{\true}(0) & = \false\,,\\
-  c_p(p \rightarrow t) & = \true\,,
-  & c_{\true}(1 \rightarrow t) & = \true\,,\\
-  c_p(pa \rightarrow t) & = a\,,\\
-  c_p(a \rightarrow t) & = a \land c_p(t)\,,
-  & c_{\true}(a \rightarrow t) & = a\,,\\
-  c_p(t_1 \oplus t_2) & = c_p(t_1) \lor c_p(t_2)\,, 
-  & c_{\true}(t_1 \oplus t_2) & = c_{\true}(t_1) \lor c_{\true}(t_2)\,.
-\end{align*}
-
-Observe that this transformation associates to each port $p \in P$ a
-causal rule $p \Rightarrow C$, where $C$ is the disjunction of all
-prefixes leading from roots of $t$ to some node containing $p$,
-including the ports of this node other than $p$.
-
-%*********************************************************************
-%*********************************************************************
-
-\section{Additional definitions for the theory of architectures}
-\label{secn:arch:appendix}
-
-This section provides the formal definitions related to priority
-models, which are omitted from the main body of the paper due to size
-limitations.
-
-\begin{definition}[Priority model]
-  \label{defn:priority}
-  A \emph{priority model} over a component interface $(V, P,
-  \export)$\footnote{%
-%
-    Notice that the export function $\export$ has no impact on the
-    priority model definition.
-%
-  } is a strict partial order on interactions: $\pi
-  \subseteq \bigl(2^P \times \guards{V} \times \updates{V} \bigr)^2$.
-
-  We write $\alpha \prec_\pi \beta$, for $(\alpha, \beta) \in \pi$, and 
-   $\filter{\alpha} \bydef{=} \bsetdef{\beta \in (2^P \times
-    \guards{V} \times \updates{V})}{\alpha \prec_\pi \beta}$, for the set of
-  interactions that have higher priority than $\alpha$.
-\end{definition}
-
-\begin{definition}[Application of priority]
-  \label{defn:priority:sem}
-  The application of a priority model $\pi$ over $(V, P, \export)$
-  to a component $B = \tuple{Q, q^0, V, \val{0}{}, P, \export, \goesto{}}$
-  is the component $\pi(B) = \tuple{Q, q^0, V, \val{0}{}, P, \export,
-  \goesto[\pi]{}}$, where $\goesto[\pi]{}$ is the minimal transition
-  relation satisfying the rule (we denote
-  $\filter[q]{\alpha} \bydef{=} %% \filter{\alpha} \cap
-  %% \bsetdef{\beta \in (2^P \times \guards{V} \times \updates{V})}
-  \setdef{\beta \in \filter{\alpha}}{q \goesto{\beta}}$)
-%
-  \begin{equation*}
-    \label{eq:priority:sem}
-%
-    \infer{
-      \alpha = (a, g, u)
-      \and
-      q \goesto{a, g, u} q'
-      \and
-      \textstyle
-      g' = g \land \bigwedge_{(b, h, w) \in \filter[q]{\alpha}} \lnot h
-    }{
-      q \goesto[\pi]{a, g', u} q'
-    }\,.
-  \end{equation*}
-%
-  %% \todoSBin{Add the intuitive explanation}
-\end{definition}
-
-\begin{definition}[Upwards compatibility]
-  \label{defn:up:compat}
-  Consider two architectures $A_i = \tuple{\cC_i, V_{A_i}, P_{A_i},
-  \export[A_i], \Gamma_i}$, for $i = 1,2$.
-%
-  We say that $A_1$ and $A_2$ are \emph{upwards compatible} iff, for
-  any two interactions $(a_i, g_i, e_i) \in \Gamma_i$, such that $a_1
-  \cap P_{A_2} = a_2 \cap P_{A_1}$ (\ie they agree on the common ports
-  of the two architectures), we have 1)~for any interaction $(b_1,
-  h_1, f_1) \in \Gamma_1$, such that $a_1 \varsubsetneq b_1$, there
-  exists an interaction $(b_2, h_2, f_2) \in \Gamma_2$, such that $a_2
-  \subseteq b_2$, $b_1 \cap P_{A_2} = b_2 \cap P_{A_1}$ and the 
-  implication  
-%
-  \begin{multline*}
-    \left(
-    \exists (q^1_C)^{C \in \supp{b_1} \cap \cC_1}:
-    \exists (q^2_C)^{C \in \supp{a_2} \cap \cC_2}:
-    \bigwedge_{
-      \begin{multlined}
-        \scriptstyle
-        C \in \supp{b_1} \cap \cC_1 \cap
-        \\
-        \scriptstyle
-        \supp{a_2} \cap \cC_2
-      \end{multlined}
-    }
-    q^1_C = q^2_C
-    \ \land
-    \right.
-    \\
-    \begin{aligned}
-      \exists \bigl(q^1_C \goesto{b_1 \cap P_C, g^{b_1}_C, f^{b_1}_C}\bigr)^{C \in \supp{b_1} \cap \cC_1}:
-      & \quad \left.
-      h_1 \land \bigwedge_{C \in \supp{b_1} \cap \cC_1} g^{b_1}_C
-      \ \land \right.
-      \\
-      \exists \bigl(q^1_C \goesto{a_1 \cap P_C, g^{a_1}_C, e^{b_1}_C}\bigr)^{C \in \supp{a_1} \cap \cC_1}:
-      & \quad \left.
-      g_1 \land \bigwedge_{C \in \supp{a_1} \cap \cC_1} g^{a_1}_C
-      \ \land \right.
-      \\
-      \exists \bigl(q^2_C \goesto{a_2 \cap P_C, g^{a_2}_C, e^{a_2}_C}\bigr)^{C \in \supp{a_2} \cap \cC_2}:
-      & \quad
-      \left.
-      g_2 \land \bigwedge_{C \in \supp{a_2} \cap \cC_2} g^{a_2}_C
-      \right) \implies 
-    \end{aligned}
-  \end{multline*}
-%
-  \begin{multline*}
-    \left(
-    \exists (q^2_C)^{C \in (\supp{b_2}\setminus\supp{a_2}) \cap \cC_2}:
-            {\color{white}\bigwedge_{C \in \cC_1}}\right. % Fake bigwedge to make the parenthesis the right size
-            \\
-            \left.
-            \exists \bigl(q^2_C \goesto{b_2 \cap P_C, g^{b_2}_C, f^{b_2}_C}\bigr)^{C \in \supp{b_2} \cap \cC_2}:
-            h_2 \land
-            \bigwedge_{C \in \supp{b_2} \cap \cC_2} g^{b_2}_C
-            \right)
-  \end{multline*}
-%  
-  holds for all valuations $\val{}{1} : V_{A_1} \rightarrow \data$
-  and $\val{}{2} : V_{A_2} \rightarrow \data$; and 2)~symmetrically
-  for any interaction $(b_2, h_2, f_2) \in \Gamma_2$, such that $a_2
-  \varsubsetneq b_2$.
-\end{definition}
-
-%****************************************************************
-%****************************************************************
-
-\section{Proofs}
-\label{secn:proofs}
-
-\begin{lemma}
-  \label{lem:onlyone}
-  Let $A = \tuple{\cC, V_A, P_A, \export[A], \Gamma}$ be an architecture and denote
-  by $\Gamma_\cC \bydef{=}
-%
-  \setdef{
-    (a \cap P_\cC, \true, \noop)
-  }{
-    (a, g, e) \in \Gamma
-  }$, with $P_\cC = \bigcup_{C \in \cC} P_C$,
-%  
-  the projection of $\Gamma$ onto the coordinators of
-  $A$.  Consider the architecture $A' = \tuple{\{C'\}, V_A, P_A, \export[A],
-  \Gamma}$, where $C' = \Gamma_\cC(\cC)$.  For any set of
-  components $\cB$, satisfying the conditions of
-  \defn{arch:application}, we have
-  $\semopen{A(\cB)} = \semopen{A'(\cB)}$.
-\end{lemma}
-%
-\begin{proof}
-  First of all, notice that, by \defn{im:sem},
-  $V_{C'} = \bigcup_{C \in \cC} V_C$ and $P_{C'} = P_\cC = \bigcup_{C \in \cC} P_C$.
-  The conditions of \defn{arch} are satisfied and $A'$ is indeed
-  an architecture.  Furthermore, $\cB$ satisfies the conditions
-  of \defn{arch:application} \wrt $A'$.  Hence, the component
-  $A'(\cB)$ is well defined.
-
-  Clearly the state spaces and initial states %% and interfaces
-  of both LTSs $\semopen{A(\cB)}$ and $\semopen{A'(\cB)}$
-  coincide.  Thus, we only have to prove that so do the
-  transition relations.  Let us assume that
-  $\cC = C_i^{i \in I}$ and $\cB = B_j^{j \in J}$.
-  We will use $q_i, q_i'$ to denote the states of
-  $C_i$ and $q_j, q_j'$ to denote the states of $B_j$,
-  and similarly for the valuations of variables.
-
-  By \defn{comp:semantics},
-%
-  \begin{equation}
-    \label{eq:lem1:trans:sem}
-    (q_i, \val{}{i})^{i \in I} (q_j, \val{}{j})^{j \in J}
-    \goesto{a, \val[\tilde]{}{}}
-    (q_i', \val{\prime}{i})^{i \in I}
-    (q_j', \val{\prime}{j})^{j \in J}
-  \end{equation}
-%  
-  is a transition in $\semopen{A(\cB)}$ (\resp
-  $\semopen{A'(\cB)}$) iff
-%
-  \begin{equation}
-    \label{eq:lem1:trans}
-    q_i^{i \in I} q_j^{j \in J}
-    \goesto{a, g', e'}
-    (q_i')^{i \in I} (q_j')^{j \in J}
-    \,,
-  \end{equation}
-%
-  is a transition in $A(\cB)$ (\resp $A'(\cB)$) and
-%
-  \begin{mathpar}
-    \val{i \in I}{i} \val{j \in J}{j}
-    \models g'
-    \,,
-    \and
-    (\val{\prime}{i})^{i \in I} (\val{\prime}{j})^{j \in J}
-    = \val[\tilde]{}{}[e']
-    \,,
-    \and
-    \valdiff{\val{i \in I}{i} \val{j \in J}{j}}{
-      \val[\tilde]{}{}} \subseteq \export(a)       
-  \end{mathpar}
-%
-  (with $\export$ defined as in \defn{arch:application}).
-
-  By \defn{im:sem} and \defn{priority:sem}, \eq{lem1:trans} is a transition in $A(\cB)$
-  iff $a \neq \emptyset$, $(a, g, e) \in \IMextend{\Gamma}{P}$,
-  where $P = \bigcup_{B \in \cB \cup \cC} P_B$, and
-  %
-  \begin{enumerate}
-  \item\label{ab:start} for $i \in I$,\\
-    $a \cap P_{C_i} \neq \emptyset$ and
-    $q_i \goesto{a \cap P_{C_i},\, g_{C_i},\, e_{C_i}} q_i'$
-    is a transition in $C_i$, or\\
-    $a \cap P_{C_i} = \emptyset$ and $q_i = q_i'$
-    (for convenience, we put $g_{C_i} = \true$ and $e_{C_i} = \noop$ in item~\ref{aux1} below);
-  \item for $j \in J$,\\
-    $a \cap P_{B_j} \neq \emptyset$ and
-    $q_j \goesto{a \cap P_{B_j},\, g_{B_j},\, e_{B_j}} q_j'$
-    is a transition in $B_j$, or\\
-    $a \cap P_{B_j} = \emptyset$ and $q_j = q_j'$
-    (for convenience, we put $g_{B_j} = \true$ and $e_{B_j} = \noop$ in item~\ref{aux1} below);
-  \item\label{ab:end}\label{aux1} $g' = g \land \bigwedge_{i \in I} g_{C_i} \land
-    \bigwedge_{j \in J} g_{B_j} \land \varphi_\mu$ and
-    $e' = e; e_{C_i}^{i \in I}, e_{B_j}^{j \in J}$, where    
-%
-    \begin{equation}
-      \label{eq:only1:maxprog:guard}
-      \varphi_\mu = \bigwedge_{
-        \begin{array}{c}
-          q_i^{i \in I} q_j^{j \in J} \goesto{b, h, f} \text{ in }
-          (\IMextend{\Gamma}{P})(\cC \cup \cB)
-          \\
-          a \varsubsetneq b
-        \end{array}
-      } \lnot h
-      \,.
-    \end{equation}
-%
-  \breakenumistart
-
-  Similarly, \eq{lem1:trans} is a transition in
-  $A'(\cB)$ iff $a \neq \emptyset$,
-  $(a, g, e) \in \IMextend{\Gamma}{P}$ and
-%
-  \breakenumiend
-% 
-  \item \label{a1b:start} \label{only1:coord}
-    $a \cap P_{C'} \neq \emptyset$ and 
-    $(q_i)^{i \in I} \goesto{a \cap P_{C'}, g_{C'}, e_{C'}} (q_i')^{i \in I}$
-    is a transition in $C'$, or\\
-    $a \cap P_{C'} = \emptyset$ and $q_i = q_i'$,
-    for all $i \in [1,m]$
-    (for convenience, we put $g_{C'} = \true$ and $e_{C'} = \noop$ in
-    item~\ref{aux2} below);
-  \item for $j \in J$,\\
-    $a \cap P_{B_j} \neq \emptyset$ and
-    $q_j \goesto{a \cap P_{B_j}, g_{B_j}, e_{B_j}} q_j'$
-    is a transition in $B_j$, or\\
-    $a \cap P_{B_j} = \emptyset$ and $q_j = q_j'$
-    (for convenience, we put $g_{B_j} = \true$ and $e_{B_j} = \noop$ in
-    item~\ref{aux2} below);
-  \item\label{aux2} $g' = g \land g_{C'} \land
-    \bigwedge_{j \in J} g_{B_j} \land \varphi_\mu'$ and
-    $e' = e; e_{C'}, e_{B_j}^{j \in J}$ (with $\varphi_\mu'$ defined as
-    in \eq{only1:maxprog:guard}, but substituting $\{C'\}$ instead of $\cC$).
-%
-  \breakenumistart
-  Notice that, for any $i \in I$, since
-  $P_{C_i} \subseteq P_{C'}$, we have
-  $a \cap P_{C_i} = (a \cap P_{C'}) \cap P_{C_i}$.
-  Thus, if $a \cap P_{C'} \neq \emptyset$, 
-  the transition in condition~\ref{only1:coord} above is
-  present in $C'$ iff
-  $(a \cap P_{C'}, \true, \noop) \in \Gamma_\cC$ and
-  \breakenumiend
-% 
-  \item for $i \in I$,\\
-    $a \cap P_{C_i} \neq \emptyset$ and
-    $q_i \goesto{a \cap P_{C_i}, g_{C_i}, e_{C_i}} q_i'$
-    is a transition in $C_i$, or\\
-    $a \cap P_{C_i} = \emptyset$ and $q_i = q_i'$,
-    (for convenience, we put $g_{C_i} = \true$ and $e_{C_i} = \noop$ in
-    item~\ref{aux3} below);
-  \item \label{a1b:end} \label{aux3} $g_{C'} = \bigwedge_{i \in I} g_{C_i}$ and
-    $e_{C'} = e_{C_i}^{i \in I}$.
-  \end{enumerate}
-
-  Consider $(a,g,e) \in \IMextend{\Gamma}{P}$.  By
-  \defn{arch:application}, this is equivalent to
-  $(a \cap P_A, g, e) \in \Gamma$.
-  Since $P_{C'} = P_\cC \subseteq P_A$, we have
-  $a \cap P_{C'} = a \cap P_\cC = (a \cap P_A) \cap P_\cC$.
-  Hence, by the definition of $\Gamma_\cC$ in the lemma statement,
-  this is also equivalent to
-  $(a \cap P_{C'}, \true, \noop) \in \Gamma_\cC$.
-
-  Thus, conditions \ref{ab:start}\ndash\ref{ab:end} are satisfied iff
-  so are conditions \ref{a1b:start}\ndash\ref{a1b:end} (to see that
-  $\varphi_\mu$ is satisfied iff so is $\varphi_\mu'$, one has to
-  consider the same two sets of conditions, but this time without the
-  additional conjuncts $\varphi_\mu$ and $\varphi_\mu'$ in
-  items~\ref{aux1} and \ref{aux2}, since no priority model is applied
-  to obtain $C'$).  This proves that the transition relations of
-  $\semopen{A(\cB)}$ and $\semopen{A'(\cB)}$ coincide and, therefore,
-  $\semopen{A(\cB)} = \semopen{A'(\cB)}$.
-\end{proof}
-
-\begin{note}
-  \label{rem:upwards:compat}
-  Notice that, since, in the statement of \lem{onlyone}, 
-  %
-  \begin{enumerate}
-  \item the interaction models are the same for both $A$ and $A'$, and
-  \item $P_{C'} = P_\cC$,
-  \end{enumerate}
-  %
-  substituting $A'$ for $A$ preserves upwards compatibility, \ie for any
-  architecture $A''$, holds the following statement: $A$ and $A''$ are
-  upwards compatible if and only if so are $A'$ and $A''$.
-\end{note}
-
-\begin{lemma}
-  \label{lem:onestep}
-  Let $\cB$ be a set of components; let $A_i = \tuple{\{C_i\}, V_{A_i},
-  P_{A_i}, \export[A_i], \Gamma_i}$, for $i = 1,2$, be two upwards compatible architectures
-  with one coordinator each, applicable to $\cB$.  Denote
-  $P_i = P_{C_i} \cup \bigcup_{B \in \cB} P_B$.
-  Finally, let
-%
-  $
-  s_1 s_2 s
-%
-  \goesto{a, \tilde{\val{}{}}}
-%
-  s_1' s_2' s'
-  $,
-%
-  be a transition in $\semopen{(A_1 \arcomp A_2)(\cB)}$, with
-  $a \neq \emptyset$, 
-  $s, s' \in \prod_{B \in \cB} S_{\semopen{B}}$
-  and
-  $s_i, s_i' \in S_{\semopen{C_i}}$ ($i=1,2$).
-%
-  Then, for $i=1,2$, either $a \cap P_i = \emptyset$ and $s_i s=
-  s_i' s'$, or there exists a transition
-%
-  $
-  s_i s
-%
-  \goesto{a \cap P_i, \val[\doubletilde]{}{}}
-%
-  s_i' s''
-  $ 
-%
-  in $\semopen{A_i(\cB)}$, with
-  $\val[\doubletilde]{}{}$ being the restriction of
-  $\val[\tilde]{}{}$ to
-  $V_i = V_{C_i} \cup \bigcup_{B \in \cB} V_B$ and
-  $s' \order s''$.
-\end{lemma}
-%
-\begin{proof}
-  By \defn{comp:semantics}, every semantic state consists of a
-  component state and a valuation of component variables.  Thus,
-  we can expand $s_1 s_2 s \goesto{a, \tilde{\val{}{}}} s_1' s_2' s'$
-  as
-%
-  \[
-  (q_1, \val{}{1}, q_2, \val{}{2}, q, \val{}{})
-%
-  \goesto{a, \tilde{\val{}{}}}
-%
-  (q_1', \val[\primeit]{}{1}, q_2', \val[\primeit]{}{1}, q', \val[\primeit]{}{})
-  \,.
-  \]
-%
-  By \defn{im:sem} and \defn{priority:sem}, this implies
-  that
-  $(q_1, q_2, q) \goesto {a, g', e'} (q_1', q_2', q')$
-  is a transition in $(A_1 \arcomp A_2)(\cB)$, with
-%
-  $g' = g \land g_1 \land g_2 \land g_\cB \land \varphi_\mu$
-  and
-  $e' = e; (e_1, e_2, e_\cB)$,
-  where $(a, g, e) \in \Gamma$ (see \eq{arch:composition} for the
-  definition of $\Gamma$);
-%  
-  $g_1$, $g_2$ and $e_1$, $e_2$ are, respectively, the guards and
-  update expressions of the underlying transitions in the coordinators
-  $C_1$ and $C_2$;
-%    
-  \begin{mathpar}
-    g_\cB = \bigwedge_{B \in \supp{a} \cap \cB} g_B
-    \,,
-    \and
-    e_\cB = e_B^{B \in \supp{a} \cap \cB}
-    \,,
-  \end{mathpar}
-%
-  are the compositions of, respectively, the guards and update
-  expressions of the operand components;
-%    
-  \begin{equation}
-    \label{eq:onestep:maxprog:guard}
-    \varphi_\mu = \bigwedge_{
-      \begin{array}{c}
-        (q_1, q_2, q) \goesto{b, h', f'} \text{ in }
-        \bigl(\IMextend{\Gamma}{(P_1 \cup P_2)}\bigr)
-        \bigl(\{C_1, C_2\} \cup \cB\bigr)
-        \\
-        a \varsubsetneq b
-      \end{array}
-    } \lnot h'
-  \end{equation}
-%
-  is the conjunct encoding the maximal progress priority in
-  \defn{priority:sem}.  As above for $g'$, for each $(b, h', f')$ in
-  \eq{onestep:maxprog:guard}, $h'$ can be decomposed as $h' = h \land
-  h_1 \land h_2 \land h_\cB$ (without the maximal progress conjunct,
-  since no priority is applied in $\bigl(\IMextend{\Gamma}{(P_1 \cup
-    P_2)}\bigr)\bigl(\{C_1, C_2\} \cup \cB\bigr)$).
-
-  By \eq{comp:semantics}, we also have
-%
-  \begin{align}
-    \label{eq:guard}
-    (\val{}{1}, \val{}{2}, \val{}{}) &\models g'
-    \,,
-    \\
-    \label{eq:substitution}
-    (\val[\primeit]{}{1}, \val[\primeit]{}{2}, \val[\primeit]{}{})
-    &= \val[\tilde]{}{}[e']
-    \,,
-    \\
-    \label{eq:transient}
-    \valdiff{(\val{}{1}, \val{}{2}, \val{}{})}{\val[\tilde]{}{}}
-    &\subseteq \export(a)
-    \,.
-  \end{align}
-%
-  If $a \cap P_1 = \emptyset$, then $\supp{a} = \{C_2\}$ and, by
-  \eq{transient} and \defn{im:sem}, $s_1 = s_1'$ and $s = s'$
-  (recall, \defn{im}, that, for $(a,g,e) \in \Gamma$, we have $e
-  \in \exprs{V_a}$).  Hereafter, assume $a \cap P_1 \neq
-  \emptyset$.
-
-  By \eq{arch:composition}, for $i=1,2$, there exist $(a \cap P_{A_i},
-  g^i, e^i) \in \Gamma_i$, such that $g = g^1 \land g^2$ and $e = e^1
-  \land e^2$.
-  %% Similarly, for each $(b, h', f')$ in \eq{onestep:maxprog:guard},
-  %% there exist $(b \cap P_{A_i}, h^i, f^i) \in \Gamma_i$, such that
-  %% $h = h^1 \land h^2$ and $f = f^1 \land f^2$.
-%
-  We want to show that the interaction $(a \cap P_1, g^1, e^1)$ is
-  enabled in the state $(q_1, \val{}{1}, q, \val{}{})$ of
-  $\semopen{A_1(\cB)}$.  To this end, we proceed in two steps:
-%
-  \begin{enumerate}
-  \item \label{onestep:proof:im} We show that $(a \cap P_1, g^1,
-    e^1)$ is enabled in the state $(q_1, \val{}{i}, q, \val{}{})$ of
-    $\semopen{(\IMextend{\Gamma_1}{P_1})(\cB)}$.
-  \item \label{onestep:proof:maxp} We show that $(a \cap P_1, g^1,
-    e^1)$ is not inhibited in $\semopen{A_1(\cB)} =
-    \semopen{\mu\bigl((\IMextend{\Gamma_1}{P_1})(\cB)\bigr)}$ by the
-    maximal progress priority.
-  \end{enumerate}
-
-  \paragraph*{Step \ref{onestep:proof:im}}
-  %% Denoting $P_\cB = \bigcup_{B \in \supp{a} \cap \cB} P_B$, 
-  By \defn{im:sem}, we have
-%
-  \begin{mathpar}
-    q_1 \goesto{a \cap P_{C_1}, g_1, e_1} q_1'
-    \and
-    \text{and}
-    \and
-    q_B \goesto{a \cap P_B, g_B, e_B} q_B',
-    \text{ for each }
-    B \in \cB
-    \,.
-  \end{mathpar}
-
-  By \eq{guard}, we have
-  $(\val{}{1}, \val{}{}) \models g^1 \land g_1 \land g_\cB$.
-
-  Denoting %% \todoSB{One tilde is enough}
-  $\val[\doubletilde]{}{1}$ the restriction of
-%
-  $\val[\tilde]{}{}$ to
-  $V_1 = V_{C_1} \cup \bigcup_{B \in \cB} V_B$,
-%
-  we have, by \eq{substitution} and the monotonicity of
-  expressions,
-%
-  $(\val[\primeit]{}{1}, \val[\primeit]{}{}) \order
-  \val[\doubletilde]{}{1}[e^1; (e_1, e_b)]$.  %% \todoSB{Remove this}\hl{Notice that all
-  %% variables affected by both $e^1$ and $e^2$ must necessarily
-  %% belong to $\bigcup_{B \in \cB} V_B$.}
-  Hence,
-%
-  $\val[\doubletilde]{}{1}[e^1; (e_1, e_b)] =
-  (\val[\primeit]{}{1}, \val[\secondit]{}{})$ with 
-  $\val[\primeit]{}{} \order \val[\secondit]{}{}$.
-
-  By \defn{comp:semantics} and \defn{im:sem}, we have
-  $
-  (q_1, \val{}{1}, q, \val{}{})
-  \goesto{a \cap P_1, \val[\doubletilde]{}{1}}
-  (q_1', \val[\primeit]{}{1}, q, \val[\secondit]{}{})
-  $ in $\semopen{(\IMextend{\Gamma_1}{P_1})(\cB)}$.
-
-  Symmetrically, we have 
-  $
-  (q_2, \val{}{2}, q, \val{}{})
-  \goesto{a \cap P_2, \val[\doubletilde]{}{2}}
-  (q_2', \val[\primeit]{}{2}, q, \val[\secondit]{}{})
-  $ in $\semopen{(\IMextend{\Gamma_2}{P_2})(\cB)}$.
-
-  \paragraph*{Step \ref{onestep:proof:maxp}}
-  Suppose that $a \cap P_1 \varsubsetneq b_1$, for some interaction
-  $(b_1, h^1, f^1) \in \IMextend{\Gamma_1}{P_1}$ enabled in $(q_1,
-  \val{}{1}, q, \val{}{})$.  Then, by upwards compatibility of $A_1$
-  and $A_2$, there exists $(b_2, h^2, f^2) \in
-  \IMextend{\Gamma_2}{P_2}$, enabled in $(q_2, \val{}{2}, q,
-  \val{}{})$, such that $a \cap P_2 \subseteq b_2$ and $b_2 \cap P_1 =
-  b_1 \cap P_2$.  By \defn{arch:application}, we have $(b_1 \cap P_{A_1},
-  h^1, e^1) \in \Gamma^1$.  Furthermore,
-%
-  \begin{multline*}
-    ((b_1 \cap P_{A_1}) \cup (b_2 \cap P_{A_2}))  \cap P_{A_1} =
-    (b_1 \cap P_{A_1}) \cup (b_2 \cap P_{A_1} \cap P_{A_2}) =\\
-    (b_1 \cap P_{A_1}) \cup ((b_2 \cap P_1) \cap P_{A_1} \cap P_{A_2}) =  
-    (b_1 \cap P_{A_1}) \cup ((b_1 \cap P_2) \cap P_{A_1} \cap P_{A_2}) =\\
-    (b_1 \cup (b_1 \cap P_2 \cap P_{A_2})) \cap P_{A_1} =
-    b_1 \cap P_{A_1} 
-  \end{multline*}
-%
-  Symmetrically, $(b_2 \cap P_{A_2}, h^2, e^2) \in \Gamma^2$ and
-  $((b_1 \cap P_{A_1}) \cup (b_2 \cap P_{A_2})) \cap P_{A_2} = b_2
-  \cap P_{A_2}$.  By \eq{arch:composition}, we then have $((b_1 \cap
-  P_{A_1}) \cup (b_2 \cap P_{A_2}), h^1 \land h^2, f^1 \expmix f^2)
-  \in \Gamma$ and, by \defn{arch:application}, $(b_1 \cup b_2, h^1 \land
-  h^2, f^1 \expmix f^2) \in \IMextend{\Gamma}{(P_1 \cup P_2)}$.
-%
-  Since both $(b_i, h^i, f^i) \in \IMextend{\Gamma_i}{P_i}$ are
-  enabled in the respective states $(q_i, \val{}{i}, q, \val{}{})$, we
-  conclude that $(b_1 \cup b_2, h^1 \land h^2, f^1 \expmix f^2)$ is
-  enabled in $(q_1, \val{}{1}, q_2, \val{}{2}, q, \val{}{})$.
-
-  Since $a \cap P_1 \varsubsetneq b_1$ and $a \cap P_2 \subseteq b_2$,
-  we have $a \varsubsetneq b_1 \cup b_2$.  Thus, $(b_1 \cup b_2, h^1
-  \land h^2, f^1 \expmix f^2)$ contribute to $\varphi_\mu$ in
-  \eq{onestep:maxprog:guard}.  Since $(b_1 \cup b_2, h^1 \land h^2,
-  f^1 \expmix f^2)$ is enabled in $(q_1, \val{}{1}, q_2, \val{}{2}, q,
-  \val{}{})$, we have $(\val{}{1}, \val{}{2}, \val{}{}) \models h^1
-  \land h^2$ and, therefore $(\val{}{1}, \val{}{2}, \val{}{})
-  \not\models \varphi_\mu$, which contradicts \eq{guard}, thereby
-  proving that $(a \cap P_1, g^1, e^1)$ is not inhibited in
-  $\semopen{A_1(\cB)} =
-  \semopen{\mu\bigl((\IMextend{\Gamma_1}{P_1})(\cB)\bigr)}$ by the
-  maximal progress priority.
-
-  The corresponding statement for $(a \cap P_2, g^2, e^2)$ is obtained
-  symmetrically.
-\end{proof}
-
-\begin{lemma}
-  \label{lem:stepabove}
-  Consider a component $B$ and let 
-%
-  $
-  (q_1, \val{}{1})
-%
-  \goesto{a, \val[\tilde]{}{}}
-%
-  (q_2, \val{}{2})
-  $,
-%
-  be a transition in $\semopen{B}$.  For any valuation
-  $\val[\primeit]{}{1}$, such that
-  $\val{}{1} \order \val[\primeit]{}{1}$ and
-  $\valdiff{\val{}{1}}{\val[\primeit]{}{1}} \subseteq \export(a)$,
-  there exists a transition
-%
-  $
-  (q_1, \val[\primeit]{}{1})
-%
-  \goesto{a, \val[\tilde]{}{}}
-%
-  (q_2, \val{}{2})
-  $
-%
-  in $\semopen{B}$.
-\end{lemma}
-%
-\begin{proof}
-  By \eq{comp:semantics}, we have
-%
-  \begin{mathpar}
-    q_1 \goesto{a, g, e} q_2
-    \,,
-    \and
-    \val{}{1} \models g
-    \,,
-    \and
-    \val{}{2} = \val[\tilde]{}{}[e]
-    \,,
-    \and
-    \text{and}
-    \and
-    \valdiff{\val{}{1}}{\val[\tilde]{}{}} \subseteq \export(a)
-    \,.
-  \end{mathpar}
-
-  By monotonicity of guards, we deduce
-  $\val[\primeit]{}{1} \models g$.
-  For any $v \not\in \export(a)$,
-  $\val[\primeit]{}{1}(v) = \val{}{1}(v) = \val[\tilde]{}{}(v)$.
-  Hence, 
-  $\valdiff{\val[\primeit]{}{1}}{\val[\tilde]{}{}}
-  \subseteq \export(a)$.
-  By \eq{comp:semantics}, we conclude 
-%
-  $
-  (q_1, \val[\primeit]{}{1})
-%
-  \goesto{a, \val[\tilde]{}{}}
-%
-  (q_2, \val{}{2})
-  $.  
-\end{proof}
-
-\begin{proof}[Proof of \thm{combining}]
-  By \lem{onlyone}, we can assume without loss of generality that each of the two
-  architectures has only one coordinator.  For $i =
-  1,2$, we denote $\{C_i\} = \cC_i$, $P_i = P_{C_i}
-  \cup\ \bigcup_{B \in \cB} P_B$ and $V_i = V_{C_i}
-  \cup\ \bigcup_{B \in \cB} V_B$.
-%
-  By \rem{upwards:compat}, this does not affect their upwards
-  compatibility, hence neither does this affect the applicability of
-  \lem{onestep} below.
-
-  The initiality of $\Phi_1 \land \Phi_2$, is trivial: both
-  $\Phi_1$ and $\Phi_2$ are initial, hence $s^0 \models \Phi_1
-  \land \Phi_2$.
-
-  Consider a path
-%
-  \[
-  s^0_1 s^0_2 s^0
-%
-  \goesto{a^1, \val[\tilde]{1}{}}
-%
-  s^1_1 s^1_2 s^1
-%
-  \goesto{a^2, \val[\tilde]{2}{}}
-  \cdots
-  \goesto{a^k, \val[\tilde]{k}{}}
-%
-  s^k_1 s^k_2 s^k
-  \]
-%
-  in $\semopen{(A_1 \arcomp A_2)(\cB)}$, where
-  $s^0,\dots,s^k \in \prod_{B \in \cB} S_{\semopen{B}}$ and
-  $s^0_i,\dots, s^k_i \in S_{\semopen{C_i}}$, for $i=1,2$.
-  We have to show that $s^k \models \Phi_1 \land \Phi_2$.
-
-  Assuming that $a^1 \cap P_1 \neq \emptyset$, by \lem{onestep},
-  there exists $s^{1\prime} \in \prod_{B \in \cB} S_{\semopen{B}}$,
-  such that
-%
-  \[
-  s^0_1 s^0
-%
-  \goesto{a^1 \cap P_1, \val[\doubletilde]{1}{}}
-%
-  s^1_1 s^{1\prime}
-  \]
-%
-  is a transition in $\semopen{A_1(\cB)}$ with
-  $\val[\doubletilde]{1}{}$ being the restriction of
-  $\val[\tilde]{1}{}$ to $V_1$ and
-  $s^1 \order s^{1\prime}$.
-%
-  By \lem{stepabove}, 
-  \[
-  s^1_1 s^1_2 s^{1\prime}
-%
-  \goesto{a^2, \val[\tilde]{2}{}}
-%
-  s^2_1 s^2_2 s^2
-  \]
-  is a transition in $\semopen{(A_1 \arcomp A_2)(\cB)}$ and,
-  therefore, 
-  \[
-  s^1_1 s^1_2 s^{1\prime}
-%
-  \goesto{a^2, \val[\tilde]{2}{}}
-%
-  s^2_1 s^2_2 s^2
-%
-  \goesto{a^3, \val[\tilde]{3}{}}
-  \cdots
-  \goesto{a^k, \val[\tilde]{k}{}}
-%
-  s^k_1 s^k_2 s^k
-  \]
-%  
-  is a path in $\semopen{(A_1 \arcomp A_2)(\cB)}$.
-%
-  Notice that, if the above assumption, $a^1 \cap P_1 \neq
-  \emptyset$, does not hold, then $s^0_1 = s^1_1$, $s^0 = s^1$
-  and we can take $s^{1\prime} = s^1$ in this latter path.
-
-  Repeating the entire argument $k-1$ times, starting with this
-  shorter path, we obtain a path
-%
-  \begin{equation}
-    \label{eq:path-in-1}
-    s^0_1 s^0
-    %
-    \goesto{a^1 \cap P_1, \val[\doubletilde]{1}{}}
-    %
-    s^1_1 s^{1\prime}
-    %
-    \goesto{a^2 \cap P_1, \val[\doubletilde]{2}{}}
-    %
-    s^2_1 s^{2\prime}
-    %
-    \goesto{a^3 \cap P_1, \val[\doubletilde]{3}{}}
-    \cdots
-    \goesto{a^k \cap P_1, \val[\doubletilde]{k}{}}
-    %
-    s^k_1 s^{k\prime}
-  \end{equation}
-%  
-  with $s^i \order s^{i\prime}$, for all $i \in [1,k]$.
-
-  From \eq{path-in-1}, we conclude that the state $s^k_1
-  s^{k\prime}$ is reachable in $\semopen{A_1(\cB)}$.  Since $A_1$
-  enforces $\Phi_1$ on $\cB$, this implies that $s^{k\prime}
-  \models \Phi_1$.  Since $s^k \order s^{k\prime}$, we deduce, by
-  \defn{property}, that $s^k \models \Phi_1$.
-
-  Symmetrically, $s^k \models \Phi_2$, which concludes
-  the proof.
-\end{proof}
-
-%*********************************************************************
-%*********************************************************************
-%
-%%\section{pNets additional definitions}
-%\label{secn:pNets:additional}
-%
-%\begin{definition}[Sorts, Holes, Leaves of pNets]
-%  \begin{itemize}
-%  \item  \noteSB{I think this can be lightened up a bit, since the definitions are all 
-%  straightforward, whereas the notation is complex.  Maybe reformulate in words and move 
-%  the formal definitions in the appendix?}
-% The sort of a pNet is its signature, i.e. the set of actions it can
-%perform. \noteSB{Is there any chance that, by writing assignments explicitly ($x := e$), 
-%we could eliminate the need to distinguish the input variables at all? That would 
-%simplify things.}\hl{In the definition of sorts, we do not need to distinguish
-%input variables} (that specify the dataflow within LTSs), so for
-%computing LTS sorts, we use a substitution operator\footnote{$\subst{y_k\gets x_k}^{k\in 
-%K}$ is the parallel substitution 
-%operation.} to remove the
-%\emph{input marker} of variables\footnote{$\overline{S}$ denotes a set of $S$.}. Formally:
-%\[
-%\begin{array}{l}
-%\Sortop(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{x \gets ?x| 
-%x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~g,~(x_j\!:= {e}_j)^{j\in
-%    J}\rangle} s'\in \to \} \\
-%\Sortop(\mylangle \overline{\pNet}\!, %\pNet_i^{i\in I}, \Sort_j^{j\in J}
-%\overline{\pNet}\!,
-%\overline{\symb{SV}}\myrangle)
-%=\{\alpha' |\, \overline{\alpha}%\alpha_j^{j\in J_k}
-%\to\alpha'\in\set{\symb{SV}}\}
-%\end{array}
-%\]
-%
-%\item
-%The set of holes of a pNet is defined inductively; the sets of holes
-%in a pNet node and its subnets are all disjoint:
-%  \[\begin{array}{l}
-%\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset \\
-%\Holes(\mylangle \pNet_i^{i\in I}\!,\Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) 
-%=J\uplus{\displaystyle \bigcup_{i\in 
-%I}\Holes(\pNet_i)}\\
-%\forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
-%\forall i_1,i_2\in I.\,i_1\neq i_2\Rightarrow  
-%\Holes(\pNet_{i_1})\cap\Holes(\pNet_{i_2})=\emptyset
-%\end{array}\]
-%\item
-%The set of leaves of a pNet is the set of all pLTSs occurring in the structure, defined 
-%inductively as:
-%\[\begin{array}{l}
-%\Leaves(\mylangle S,s_0, \to\myrangle) \!=\!\emptyset\\%\{\mylangle S,s_0, \to\myrangle\}\\
-%\Leaves(\mylangle \pNet_i^{i\in I}\!,%Sort_j^{j\in J}
-%\overline{\Sort}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \biguplus_{i\in 
-%I}\Leaves(\pNet_i)\uplus\{i\mapsto \pNet_i|\pNet_i\pNet_i \text{ is a }\pLTS\}}
-%\end{array}\]
-%\end{itemize}
-%\end{definition}
-
-%*********************************************************************
-%*********************************************************************
-
-\section{Additional material for the case study}
-
-\subsection{Properties enforced by the Failure Monitor architecture}
-\label{secn:properties}
-
-The architecture in \fig{schema:ArchFailure:BIP} enforces the
-following safety properties:
-\begin{enumerate}
-\item There is always a possibility to reset the system
-  after a single failure (\ie without additional failures
-  having to occur in the meantime):
-  \begin{equation}
-    \label{eq:prop:reset:can}
-    \AG \bigl(\PortFail \rightarrow \EX \EU[]{\lnot \PortFail}{\PortReset}\bigr).
-  \end{equation}
-
-  \noteIn{Checking this on the resulting open automaton should be understood after application of the encoding, namely here the original ``fail'' event must be an effective ``fail'' of the hole ``B'', that is a ``fail(true)'' action in the automaton.}
-
-\item As long as no failure has occured, the $z$ variable of the
-  $\NameTimer$ component has the value $\topinterval$:
-  \begin{equation}
-    \label{eq:prop:z:top}
-    \AW[\quad]{(z = \topinterval)}{\PortFail} \land\quad
-    \AG \bigl(
-    \PortReset \rightarrow \AW[]{(z = \topinterval)}{\PortFail}
-    \bigr).
-  \end{equation}
-
-\item A reset can only be requested within the specified delay after
-  a failure:
-  \begin{multline}
-    \label{eq:prop:to:delay}
-    \forall T_0, T_1 \in \sZ,\
-    \AG \Big((\PortFail \land \NameTimer.t = T_0) \rightarrow
-    \\
-    \AW[]{\bigl((\PortAsk \land \NameTimer.t = T_1) \rightarrow
-      (T_1 - T_0 \in \NameCtrl.\mathit{zone})\bigr)
-    }{
-      (\PortReset \lor \PortResume)
-    }\Big),
-  \end{multline}
-  where $T_0$ and $T_1$ are integer parameters.  (The formula
-  holds with the universal quantification over $T_0$ and $T_1$
-  due to the fact that their individual values only appear in
-  the left-hand sides of the two implications.)
-\end{enumerate}
-
-In addition\mdash although outside the scope of this paper\mdash it
-enforces the \emph{liveness} property \emph{``Whenever a reset is
-  requested, it will eventually be effectuated''}:
-%
-  \begin{equation}
-    \label{eq:prop:reset:will}
-    \AG (\PortAsk \rightarrow \AF \PortReset).
-  \end{equation}
-%
-  (See \cite{AttieBBJS16-architectures-faoc} for the definition and
-  results on the preservation of liveness properties by composition of
-  architectures in absence of data and priorities.)
-
-\subsection{Output of the open-automaton construction}
-\label{secn:full-results}
-
-We first show the input pNet, with its 5 synchronisation vectors, and 2 controllers.
-
-\bigskip
-\noindent
-\verbatimfont{\small}
-\begin{verbatim}
-SV0: <tick(z, t, z1), fail(zone, b1), fail(b0), _> --> fail(b0),
-         [(b1->b0)/\(z1=z |Intersection| ((b1?zone:TopInt)+t))]
-SV1: <cancel(b1), resume(b2), resume, _> --> resume, (b1=b2)
-SV2: <timeout, timeout, _, ask> --> ask
-SV3: <_, reset, _, reset> --> reset
-SV4: <init, init, _, _> --> init
-pLTS: Timer
-- Transition: t0---init-->t1, { t := 0 z := TopInt}
-- Transition: t1---tick(z, t, z1)-->t1, [(t<GET_MAX z)], { t := (t+1) z := z1}
-- Transition: t1---cancel(false)-->t1, {}
-- Transition: t1---cancel(true)-->t1, { t := 0 z := TopInt}
-- Transition: t1---timeout-->t1, [t in z], { t := (t+1)}
-pLTS: Control
-- Transition: s0---init-->s1, { zone := minZone,maxZone}
-- Transition: s1---timeout-->s1, {}
-- Transition: s1---resume(false)-->s1, {}
-- Transition: s1---fail(zone, false)-->s1, {}
-- Transition: s1---fail(zone, true)-->s2, {}
-- Transition: s2---fail(zone, false)-->s2, {}
-- Transition: s2---resume(false)-->s2, {}
-- Transition: s2---resume(true)-->s1, {}
-- Transition: s2---timeout-->s3, {}
-- Transition: s3---fail(zone, false)-->s3, {}
-- Transition: s3---resume(false)-->s3, {}
-- Transition: s3---reset-->s1, {}
-Holes: B
-Holes: E
-\end{verbatim}
-\bigskip
-
-Then some of the twelve generated OTs in their verbatim form. In this format
-the first element of the premisse is a list of the moves of the pLTS
-participating in the transition. This is not part of the OT, but
-provides a trace of its construction. Also, the variables occuring in
-the actions and predicate expressions have names helping to understand
-where they come from (e.g. \verb|b0:sva_SV0| in $OT2$ below).
-This is not a full ``proof-carrying
-code'', but it allows for a better understanding of the construction
-of each OT.
-
-\bigskip
-\verbatimfont{\small}
-\begin{verbatim}
-   {t0---init-->t1, s0---init-->s1},   {},  [true],
-   {t := 0, z := TopInt, zone := minZone,maxZone}
-OT1 ------------------------------------------------------------
-    <t0_s0>-----init----><t1_s1>
-
-   {t1---tick(z, t, z1)-->t1, s1---fail(zone, false)-->s1},   {---:hb_B-->},
-   [(:hb_B=fail(b0:sva_SV0)/\(t<(GET_MAX z))
-     /\((tick(z, t, z1))=(tick(z:sva_SV0, t:sva_SV0, z1:sva_SV0)))
-     /\((fail(zone, false))=(fail(zone:sva_SV0, b1:sva_SV0)))
-     /\(b1:sva_SV0=>b0:sva_SV0)
-     /\(z1:sva_SV0=
-     (z:sva_SV0  |Intersection| ((b1:sva_SV0?(zone:sva_SV0)TopInt))+t:sva_SV0)))],
-   {t := t+1, z := z1}
-OT2 ------------------------------------------------------------
-    <t1_s1>-----fail(b0:sva_SV0)----><t1_s1>
-
-   {t1---tick(z, t, z1)-->t1, s1---fail(zone, true)-->s2},   {---:hb_B-->},
-   [(:hb_B=fail(b0:sva_SV0)/\(t<(GET_MAX z))
-     /\((tick(z,t, z1))=(tick(z:sva_SV0, t:sva_SV0, z1:sva_SV0)))
-     /\((fail(zone, true))=(fail(zone:sva_SV0, b1:sva_SV0)))
-     /\(b1:sva_SV0=>b0:sva_SV0)
-     /\(z1:sva_SV0=
-     (z:sva_SV0  |Intersection| ((b1:sva_SV0?(zone:sva_SV0)TopInt))+t:sva_SV0)))],
-   {t := t+1, z := z1}
-OT3 ------------------------------------------------------------
-    <t1_s1>-----fail(true)----><t1_s2>
-
-   {t1---cancel(false)-->t1, s1---resume(false)-->s1},   {---:hb_B-->},
-   [(:hb_B=fail(b0:sva_SV0)
-     /\((cancel(false))=(cancel(b1:sva_SV1)))
-     /\((resume(false))=(resume(b2:sva_SV1)))
-     /\(b1:sva_SV1=b2:sva_SV1)],   {}
-OT4 ------------------------------------------------------------
-    <t1_s1>-----resume----><t1_s1>
-
-INFO  BIPArchFailureTimerMax - Total: 12 SATISFIABLE OTs
-INFO  BIPArchFailureTimerMax -        235 UNSATISFIABLE OTs
-INFO  BIPArchFailureTimerMax - Total Time: 1293 ms
-\end{verbatim}
-\bigskip
-
-%%    {t1---timeout-->t1, s1---timeout-->s1},   {---:hb_E-->},
-%%    [(:hb_E=ask)/\(t in z)],   {t := t+1}
-%% OT5 ------------------------------------------------------------
-%%     <t1_s1>-----ask----><t1_s1>
-
-%%    {t1---tick(z, t, z1)-->t1, s2---fail(zone, false)-->s2},   {---:hb_B-->},
-%%    [(:hb_B=fail(b0:sva_SV0)/\(t<(GET_MAX z))
-%%      /\((tick(z, t, z1))=(tick(z:sva_SV0, t:sva_SV0, z1:sva_SV0)))
-%%      /\((fail(zone, false))=(fail(zone:sva_SV0, b1:sva_SV0)))
-%%      /\(b1:sva_SV0=>b0:sva_SV0)
-%%      /\(z1:sva_SV0=
-%%      (z:sva_SV0  |Intersection| ((b1:sva_SV0?(zone:sva_SV0)TopInt))+t:sva_SV0)))],
-%%    {t := t+1, z := z1}
-%% OT6 ------------------------------------------------------------
-%%     <t1_s2>-----fail(b0:sva_SV0)----><t1_s2>
-
-%%    {t1---cancel(false)-->t1, s2---resume(false)-->s2},   {---:hb_B-->},
-%%    [(:hb_B=resume)/\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
-%%      /\((resume(false))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],
-%%    {}
-%% OT7 ------------------------------------------------------------
-%%     <t1_s2>-----resume----><t1_s2>
-
-%%    {t1---cancel(true)-->t1, s2---resume(true)-->s1},   {---:hb_B-->},
-%%    [(:hb_B=resume)/\((cancel(true))=(cancel(b1:sva_SV1:1:2)))
-%%      /\((resume(true))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],
-%%    {t := 0, z := TopInt}
-%% OT8 ------------------------------------------------------------
-%%     <t1_s2>-----resume----><t1_s1>
-
-%%    {t1---timeout-->t1, s2---timeout-->s3},   {---:hb_E-->},
-%%    [(:hb_E=ask)/\(t in z)],   {t := t+1}
-%% OT9 ------------------------------------------------------------
-%%     <t1_s2>-----ask----><t1_s3>
-
-%%    {t1---tick(z, t, z1)-->t1, s3---fail(zone, false)-->s3},   {---:hb_B-->},
-%%    [(:hb_B=fail(b0:sva_SV0)/\(t<(GET_MAX z))
-%%      /\((tick(z, t, z1))=(tick(z:sva_SV0, t:sva_SV0, z1:sva_SV0)))
-%%      /\((fail(zone, false))=(fail(zone:sva_SV0, b1:sva_SV0)))
-%%      /\(b1:sva_SV0=>b0:sva_SV0)
-%%      /\(z1:sva_SV0=
-%%      (z:sva_SV0  |Intersection| ((b1:sva_SV0?(zone:sva_SV0)TopInt))+t:sva_SV0)))],
-%%    {t := t+1, z := z1}
-%% OT10 ------------------------------------------------------------
-%%     <t1_s3>-----fail(b0:sva_SV0)----><t1_s3>
-
-%%    {t1---cancel(false)-->t1, s3---resume(false)-->s3},   {---:hb_B-->},
-%%    [(:hb_B=resume)/\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
-%%      /\((resume(false))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],   {}
-%% OT11 ------------------------------------------------------------
-%%     <t1_s3>-----resume----><t1_s3>
-
-%%     {s3---reset-->s1},   {---:hb_E-->},     [(:hb_E=ask)],   {}
-%% OT12 ------------------------------------------------------
-%%     <t1_s3>-----reset----><t1_s1>
-
-Now we list the full set of OTs, in latex form, for better
-readability. This comes as a complement to the open automaton in
-\fig{ArchFailure:OA-annex}, in which we only have a partial view
-of the OTs details.
-
-\begin{figure}[t]
-  \centering
-  \includegraphics[width=\columnwidth]{TimerOAFullDetailed}
-  \caption{The open Automaton of the Failure Monitor Architecture}
-  \label{fig:ArchFailure:OA-annex}
-\end{figure}
-
-\bigskip
-\noindent
-$  OT_1  = \openrule
-{\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
-{\ostate{00} \OTarrow{init} \ostate{11}}
-$
-
-\medskip    
-\noindent
-$  OT_2  = \openrule
-{\{B\mapsto fail(b0)\},\\
-  t<GetMax(z) \land b1=false \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),\\
-  \{z:=z1\} }
-{\ostate{11} \OTarrow{fail} \ostate{11}}
-$
-\medskip
-
-\noindent
-  $  OT_3  = \openrule
-  {\{B\mapsto fail(b0)\},\\
-    t<GetMax(z) \land b1=true \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),\\
-    \{z:=z1\} }
-  {\ostate{11} \OTarrow{fail} \ostate{12}}
-  $
-  \medskip
-
-\noindent
-  $  OT_4  = \openrule
-  {\{B\mapsto resume\},
-    b1=false \land b2=false \land b1=b2
-    \{\}  }
-  {\ostate{11} \OTarrow{resume} \ostate{11}}
-  $
-  \medskip
-
-\noindent
-  $  OT_5  = \openrule
-  {\{E\mapsto ask\},
-    t \in z,
-    \{t:=t+1\}  }
-  {\ostate{11} \OTarrow{ask} \ostate{11}}
-  $
-  \medskip
-
-\noindent
-  $  OT_6  = \openrule
-  {\{B\mapsto fail(b0)\},\\
-    t<GetMax(z) \land b1=false \land b1=>b0 \land z1=(z \cap (b1?zone;TopInt)+t),\\
-    \{t:=t+1, z:=z1\} }
-  {\ostate{12} \OTarrow{fail} \ostate{12}}
-  $
-  \medskip
-
-\noindent
-  $  OT_7  = \openrule
-  {\{B\mapsto resume\},
-    b1=false \land b2=false \land b1=b2,
-    \{\} }
-  {\ostate{12} \OTarrow{resume} \ostate{12}}
-  $
-  \medskip
-
-\noindent
-  $  OT_8  = \openrule
-  {\{B\mapsto resume\},
-    b1=true \land b2=true \land b1=b2, 
-    \{t:=0, z:=TopInt\} }
-  {\ostate{12} \OTarrow{resume} \ostate{11}}
-  $
-  \medskip
-
-\noindent
-  $  OT_9  = \openrule
-  {\{E\mapsto ask\},
-    t \in z,
-    \{t:=t+1\} }
-  {\ostate{12} \OTarrow{ask} \ostate{13}}
-  $
-  \medskip
-
-\noindent
-  $  OT_{10}  = \openrule
-  {\{B\mapsto fail(b0)\},\\
-    t<GetMax(z) \land b1=false \land b1=>b0 \land z1=(z \cap (b1?zone;TopInt)+t),\\
-    \{t:=t+1, z:=z1\} }
-  {\ostate{13} \OTarrow{fail} \ostate{13}}
-  $
-  \medskip
-
-\noindent
-  $  OT_{11}  = \openrule
-  {\{B\mapsto resume\},
-    b1=false \land b2=false \land b1=b2,
-    \{\} }
-  {\ostate{13} \OTarrow{resume} \ostate{13}}
-  $
-  \medskip
-
-\noindent
-  $  OT_{12}  = \openrule
-  {\{E\mapsto reset\},
-    true,
-    \{\} }
-  {\ostate{13} \OTarrow{reset} \ostate{11}}
-  $
-
-  \medskip
-
-  \paragraph{Properties.}
-
-  In \fig{ArchFailure:OA-annex}, you can see that some
-  properties from appendix \app{properties} do not hold.
-
-  In particular, the first safety property \eq{prop:reset:can}:
-  \begin{equation*}
-    \AG \bigl(\PortFail(true) \rightarrow \EX \EU[]{\lnot \PortFail(true)}{\PortReset}\bigr).
-  \end{equation*}
-is not true, because the $OT_2$ loop on state $\ostate{11}$ stays in
-state 11 where you need another $\PortFail(true)$ before enabling a
-reset. This is because without priorities we can have an
-activity on the dangling ``fail'' port without synchronising with the
-others, even if they are available.
-
-This can be solved by the version with the Max Progress encoding.
-This modifies both the pLTS transitions, and the synchronisation
-vectors, as shown below:
-
-\bigskip
-\small\begin{verbatim}
-SV0: <tick(z, t, z1), fail(zone, bf, b1), fail(b0), _> --> fail(b0),
-         [(b1=>b0)/\((bf/\b0)=>b1)/\(z1=(z |Intersection| ((b1?zone:TopInt)+t)))]
-SV1: <cancel(bc, b1), resume(br, b2), resume, _>-->resume, (b1=b2)/\((bc/\br)=>(b1/\b2))
-SV2: <timeout, timeout, _, ask> --> ask
-SV3: <_, reset, _, reset> --> reset
-SV4: <init, init, _, _> --> init
-
-pLTS: Timer
-- Transition: t0---init-->t1, { t := 0 z := TopInt}
-- Transition: t1---tick(z, t, z1)-->t1, [t<(GET_MAX z)], { t := t+1 z := z1}
-- Transition: t1---cancel(true, false)-->t1, {}
-- Transition: t1---cancel(true, true)-->t1, { t := 0 z := TopInt}
-- Transition: t1---timeout-->t1, [t in z], { t := 0 z := TopInt}
-pLTS: Control
-- Transition: s0---init-->s1, { zone := minZone,maxZone}
-- Transition: s1---timeout-->s1, {}
-- Transition: s1---resume(false, false)-->s1, {}
-- Transition: s1---fail(zone, true, false)-->s1, {}
-- Transition: s1---fail(zone, true, true)-->s2, {}
-- Transition: s2---fail(zone, false, false)-->s2, {}
-- Transition: s2---resume(true, false)-->s2, {}
-- Transition: s2---resume(true, true)-->s1, {}
-- Transition: s2---timeout-->s3, {}
-- Transition: s3---fail(zone, false, false)-->s3, {}
-- Transition: s3---resume(false, false)-->s3, {}
-- Transition: s3---reset-->s1, {}
-\end{verbatim}
-\bigskip
-
-  The new OA is shown in \fig{ArchFailure:OA-MaxProgress}.
-
-  \begin{figure}[t]
-  \centering
-  \includegraphics[width=\columnwidth]{TimerOAMaxProgress}
-  \caption{The open Automaton of the Failure Monitor Architecture,
-    with Maximal Progress}
-  \label{fig:ArchFailure:OA-MaxProgress}
-\end{figure}
-
-\begin{itemize}
-\item $OT_2$ and $OT_{10}$ have changed because $b0=true$ is no longer possible
-\item $OT_7$ has disappeared because it is now unsat.
-\end{itemize}
-
-  Here we give the detail of the modification of $OT_2$:
-
-\bigskip
-\begin{verbatim}
-  {t1---tick(z, t, z1)-->t1, s1---fail(zone, true, false)-->s1},
-  {B|->fail(b0:sva_SV0)},
-    [(t<(GET_MAX z))
-     /\((tick(z, t, z1))=(tick(z:sva_SV0, t:sva_SV0, z1:sva_SV0)))
-     /\((fail(zone, true, false))=(fail(zone:sva_SV0, bf:sva_SV0, b1:sva_SV0)))
-     /\(b1:sva_SV0=>b0:sva_SV0)
-     /\((bf:sva_SV0/\b0:sva_SV0)=>b1:sva_SV0)
-     /\(z1:sva_SV0=(z:sva_SV0 |Intersection|
-                    ((b1:sva_SV0?(zone:sva_SV0):(TopInt))+t:sva_SV0)))],
- {t := t+1, z := z1}
-OT:2 ------------------------------------------------------------
-     <t1_s1>-----fail(b0:sva_SV0)----><t1_s1>
-\end{verbatim}
-\bigskip
-
-As \verb|bf| is true, and \verb|b1| is false, the predicate fragment
-\verb|((bf/\b0)=>b1)| imposes that \verb|b0| is false.
-
-%% \subsubsection{Scaling-up: composing architectures.}
-
-%% Here is the code of the corresponding composed pNet:
-%% %% \noteEMin{Il faudrait (mais a-t-on le temps?): faire un dessin de la
-%% %%   composition au niveau BIP, et au niveau pNet. Un resultat brut, vaguement
-%% %%   correct, montre 37 OTs, modulo les petites questions de mon mail de
-%% %%   mercredi midi...}
-
-%% %% \todoSBin{Ecrire les proprietes qu'il doit verifier... ? }
-
-%% \bigskip
-%% \begin{verbatim}
-%% SV0: <tick(z, t, z1), fail(zone1, b11), fail(zone2, b12), fail1(b01), fail2(b02), _> 
-%%      --> fail(b01, b02), 
-%%      [(z1 = z |Intersection| ((b11?zone1:TopInt)+t) |Intersection| ((b12?zone2:TopInt)+t))
-%%       /\(b11=>b01)/\(b12=>b02)]
-%% SV1: <cancel(b1), resume(b21), resume(b22), resume1, resume2, _>-->resume, 
-%%      [(b1=b21)/\(b1=b22)]
-%% SV2: <timeout, timeout, timeout, _, _, ask>-->ask
-%% SV3: <_, reset, reset, _, _, reset>-->reset
-%% SV4: <init, init, init, _, _, _>-->init
-
-%% pLTS: Timer
-%% - Transition: t0---init-->t1, { t := 0 z := TopInt}
-%% - Transition: t1---tick(z, t, z1)-->t1, [t<(GET_MAX z)], { t := t+1 z := z1}
-%% - Transition: t1---cancel(false)-->t1, {}
-%% - Transition: t1---cancel(true)-->t1, { t := 0 z := TopInt}
-%% - Transition: t1---timeout-->t1, [t in z], { t := 0 z := TopInt}
-
-%% pLTS: FC1
-%% - Transition: s0---init-->s1, { zone1 := minZone1,maxZone1}
-%% - Transition: s1---timeout-->s1, {}
-%% - Transition: s1---resume(false)-->s1, {}
-%% - Transition: s1---fail(zone1, false)-->s1, {}
-%% - Transition: s1---fail(zone1, true)-->s2, {}
-%% - Transition: s2---fail(zone1, false)-->s2, {}
-%% - Transition: s2---resume(false)-->s2, {}
-%% - Transition: s2---resume(true)-->s1, {}
-%% - Transition: s2---timeout-->s3, {}
-%% - Transition: s3---fail(zone1, false)-->s3, {}
-%% - Transition: s3---timeout-->s3, {}
-%% - Transition: s3---resume(false)-->s3, {}
-%% - Transition: s3---reset-->s1, {}
-
-%% pLTS: FC2
-%% - Transition: s0---init-->s1, { zone2 := minZone2,maxZone2}
-%% - Transition: s1---timeout-->s1, {}
-%% - Transition: s1---resume(false)-->s1, {}
-%% - Transition: s1---fail(zone2, false)-->s1, {}
-%% - Transition: s1---fail(zone2, true)-->s2, {}
-%% - Transition: s2---fail(zone2, false)-->s2, {}
-%% - Transition: s2---resume(false)-->s2, {}
-%% - Transition: s2---resume(true)-->s1, {}
-%% - Transition: s2---timeout-->s3, {}
-%% - Transition: s3---fail(zone2, false)-->s3, {}
-%% - Transition: s3---timeout-->s3, {}
-%% - Transition: s3---resume(false)-->s3, {}
-%% - Transition: s3---reset-->s1, {}
-
-%% INFO  BIPArchFailureTimerMaxV4X2 - Total: 37 SATISFIABLE OTs
-%% INFO  BIPArchFailureTimerMaxV4X2 -        3136 UNSATISFIABLE OTs
-%% INFO  BIPArchFailureTimerMaxV4X2 - Total Time: 9111 ms
-%% \end{verbatim}
-
-%% \bigskip
-%% \Fig{ArchFailure:OA-TimerV4X2} shows the open automata of
-%% this composed architecture.
-%% Note that e..g. the open transition labelled ``$fail(*,tt)$'' stands for
-%% ``$fail(b01,b02)$'', where  $b01'$ can be arbitrarily true or
-%% false. As in the previous case, this is because we have not use here
-%% the Max Progress hypothesis, otherwise all the ``*'' in the figure
-%% should be replaced by ``$ff$''.
-
-%%   \begin{figure}[t]
-%%   \centering
-%%   \includegraphics[width=0.8\columnwidth]{TimerV4X2}
-%%   \caption{The open Automaton of the composed system}
-%%   \label{fig:ArchFailure:OA-TimerV4X2}
-%% \end{figure}
-
-\end{document}

### 2019-04-29 2016-Weak-FH-Bisim/WeakBisim.tex

@@
        	\land \alpha\!=\!\alpha_{px} \land
-       	\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)$\\
+       	\Pred_{{px}}\subst{\Post_{OT}\shortotimes\Post_{OT_{px}}}\right)$\\
 
@@
        	\land \alpha_{px}\!=\!\alpha_{pxy} \land
-       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.\\
+       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}\shortotimes\Post_{OT_{pxy}}}\right)$.\\
 
@@
 \end{mathpar}
+\TODO{changer alpha...}
 where\\
@@
      \land \alpha \!=\! \alpha_{x y} \land  
-     \Pred_{s',t_{x y z}}\subst{\Post_{OT}}\subst{\Post\,}\right)$
+     \Pred_{s',t_{x y z}}\subst{\Post_{OT}\shortotimes\Post\,}\right)$
 We recall that we have:\\
-$\Pred_{OT}= \Pred^1 \wedge \Pred^2\subst{\Post^1} \wedge \Pred^3\subst{\Post^2}\subst{\Post^1}$\\
-$\Post_{OT}=\Post^3\subst{\Post^2}\subst{\Post^1}$\\
+$\Pred_{OT}= \Pred^1 \wedge \Pred^2\subst{\Post^1} \wedge \Pred^3\subst{\Post^2\shortotimes\Post^1}$\\
+$\Post_{OT}=\Post^3\subst{\Post^2\shortotimes\Post^1}$\\
 Let's start with the statement:\\
@@
      \land \alpha_x\!=\!\tau \land  
-     \Pred_{s_1^1,t_x}\subst{\Post^1}\subst{\Post_{OT_x}}\right)$\\
+     \Pred_{s_1^1,t_x}\subst{\Post^1\shortotimes\Post_{OT_x}}\right)$\\
 The conjunction of the term $\Pred^2\subst{\Post^1}$ with the both sides of the implication, we get:\\  
@@
      \land \alpha_x\!=\!\tau \land  
-     \Pred_{s_1^1,t_x}\subst{\Post^1}\subst{\Post_{OT_x}}\right) \wedge\Pred^2\subst{\Post^1} \subst{\Post_{OT_x}}  \\
+     \Pred_{s_1^1,t_x}\subst{\Post^1\shortotimes\Post_{OT_x}}\right) \wedge\Pred^2\subst{\Post^1\shortotimes\Post_{OT_x}}  \\
 $
@@
 \!\!   \left(\forall j\in J_x. \vis{\beta^1_j}\!=\!\gamma_{jx}\Rightarrow \Pred_{OT_x}
-     \!\land\! \alpha_x\!=\!\tau\land(\Pred_{s_1^1,t_x}\wedge\Pred^2)\subst{\Post^1}\subst{\Post_{OT_x}} \right)$\\
+     \!\land\! \alpha_x\!=\!\tau\land(\Pred_{s_1^1,t_x}\wedge\Pred^2)\subst{\Post^1\shortotimes\Post_{OT_x}} \right)$\\
 By replacing the inner sub-term $(\Pred_{s_1^1,t_x}\wedge\Pred^2)$ by the consequent of the corresponding implication given in case 2,  the formula becomes: \\
@@
 \vis{\beta^2_j}\!\!=\!\!\gamma_{jx y}\Rightarrow\\~~\qquad\quad \Pred_{OT_{x y}}\land \alpha\!=\!\alpha_{x y}\!
-\land \Pred_{s_1^2,t_{x y}}\subst{\Post^2}\subst{\Post_{OT_{x y}}})\Big)\subst{\Post^1} \subst{\Post_{OT_x}} \Big)$\\
+\land \Pred_{s_1^2,t_{x y}}\subst{\Post^2\shortotimes\Post_{OT_{x y}}})\Big)\subst{\Post^1\shortotimes\Post_{OT_x}} \Big)$\\
 Furthermore, the rewriting of the implication  gives:\\
@@
 \vis{\beta^1_j}\!\!=\!\!\gamma_{jx} \land  \forall j \in J_{x y}.
-\vis{\beta^2_j}\!\!=\!\gamma_{jx y}\Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \\\subst{\Post^1} \subst{\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \land \Pred_{s_1^2,t_{x y}}\subst{\Post^2}\subst{\Post^1}\subst{\Post_{OT_{x y}}} \subst{\Post_{OT_x}}\Big)$\\
-Finally, the conjunction with the term $\Pred^3\subst{\Post^2}\subst{\Post^1}$ of the both sides of the implication and rewriting, we get:\\
-$(\Pred_{s,t} \land \Pred^1)\wedge\Pred^2\subst{\Post^1} \land \Pred^3\subst{\Post^2}\subst{\Post^1}\\
+\vis{\beta^2_j}\!\!=\!\gamma_{jx y}\Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \\\subst{\Post^1\shortotimes\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \land \Pred_{s_1^2,t_{x y}}\subst{\Post^2\shortotimes\Post^1\shortotimes \Post_{OT_{x y}}\shortotimes \Post_{OT_x}}\Big)$\\
+Finally, the conjunction with the term $\Pred^3\subst{\Post^2\shortotimes\Post^1}$ of the both sides of the implication and rewriting, we get:\\
+$(\Pred_{s,t} \land \Pred^1)\wedge\Pred^2\subst{\Post^1} \land \Pred^3\subst{\Post^2\shortotimes\Post^1}\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} 
@@
 \vis{\beta^2_j}\!=\!\gamma_{jx y} \Rightarrow \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \alpha_x\!=\!
-\tau \land \alpha\!=\! \alpha_{x y} \land (\Pred_{s_1^2,t_{xy}} \land  \Pred^3) \subst{\Post^2}
-\subst{\Post^1}\subst{\Post_{OT_{x y}}} 
-\subst{\Post_{OT_x}} \Big)$\\ 
-Again because of the domain independence of the substitution, we deleted $\subst{\Post^1}$, and  we have added  $\subst{\Post_{OT_{x y}}}\subst{\Post_{OT_x}}$ on the right side of the implication.
+\tau \land \alpha\!=\! \alpha_{x y} \land (\Pred_{s_1^2,t_{xy}} \land  \Pred^3) \subst{\Post^2\shortotimes \Post^1\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$\\ 
+Again because of the domain independence of the substitution, we deleted $\subst{\Post^1}$, and  we have added  $\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}$ on the right side of the implication.
 Finally, by replacing $(\Pred_{s_1^2,t_{xy}} \land  \Pred^3)$
 by the consequent of the corresponding implication given in case 3, we get:\\
-$(\Pred_{s,t} \land \Pred^1)\land \Pred^2\subst{\Post^1} \land \Pred^3\subst{\Post^2}\subst{\Post^1}\\
+$(\Pred_{s,t} \land \Pred^1)\land \Pred^2\subst{\Post^1} \land \Pred^3\subst{\Post^2\shortotimes\Post^1}\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} \displaystyle{\bigvee_{z\in Z}} 
@@
 J_{x y z}.
-\vis{\beta^3_j}\!\!=\!\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\!\subst{\Post_{OT_{x y}}} \subst{\Post_{OT_x}} \land \alpha_x\!=\!
-\tau \!\land \alpha\!=\!\alpha_{x y} \land \alpha_{x y z}\!=\!\tau \land \Pred_{s^3_1,t_{x y z}}  \underbrace{\subst{\Post^3}\subst{\Post^2}
-\subst{\Post^1}}_{\subst{\Post_{OT}}}\subst{\Post_{OT_{x y z}}}\subst{\Post_{OT_{x y}}} \subst{\Post_{OT_x}} \Big)$
+\vis{\beta^3_j}\!\!=\!\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\!\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \land \alpha_x\!=\!
+\tau \!\land \alpha\!=\!\alpha_{x y} \land \alpha_{x y z}\!=\!\tau \land \Pred_{s^3_1,t_{x y z}}  \subst{\underbrace{\Post^3\shortotimes\Post^2\shortotimes\Post^1}_{\Post_{OT}}\shortotimes \Post_{OT_{x y z}}\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$
 Therefore, having $s^3_1=s'$ we can conclude:\\
-$(\Pred_{s,t} \land \Pred^1)\land \Pred^2\subst{\Post^1} \land \Pred^3\subst{\Post^2}\subst{\Post^1}\\
+$(\Pred_{s,t} \land \Pred^1)\land \Pred^2\subst{\Post^1} \land \Pred^3\subst{\Post^2\shortotimes\Post^1}\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} \displaystyle{\bigvee_{z\in Z}} 
 \Big(\forall j\in J_{x y z}.
-\vis{\beta^1_j}.\vis{\beta^2_j}.\vis{\beta^3_j}\!=\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}} \subst{\Post_{OT_x}} \land \alpha\!=\!\alpha_{x y} \land \Pred_{s',t_{x y z}}\subst{\Post_{OT}}\subst{\Post_{OT_{x y z}}}\subst{\Post_{OT_{x y}}} \subst{\Post_{OT_x}} \Big)$
+\vis{\beta^1_j}.\vis{\beta^2_j}.\vis{\beta^3_j}\!=\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \land \alpha\!=\!\alpha_{x y} \land \Pred_{s',t_{x y z}}\subst{\Post_{OT}\shortotimes\Post_{OT_{x y z}}\shortotimes\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$
 This is exactly what we needed to prove. \qed
@@
 $s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
+$\displaystyle{
+\set{\gamma}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}\subst{\bigotimes_{j=i-1}^{0} \Post_j^1 } }  \dotcup  \vis{\set{\beta^2}\subst{\bigotimes_{j=n}^{0}\Post_j^1}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i} \subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=m_1}^{0}\Post^1_j} }}
+\\
+\Pred=\bigwedge_{i=0}^{m_1}\Pred^1_i\subst{\bigotimes_{j=i-1}^{0}\Post_j^1}\land\Pred^2 \subst{\bigotimes_{j=m_1}^{0}\Post_j^1}\land\\ 
+~\qquad\quad\Big(\bigwedge_{i=0}^{m_2}\Pred_i^3\subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=m_1}^{0}\Post^1_j}\Big)\\
+\Post=\bigotimes_{j=m_2}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=m_1}^{0}\Post^1_j$
+
+------------------------
+
 $\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i}}}\\

### 2019-04-29 2016-Weak-FH-Bisim/WeakBisim.tex
part 2

@@
 		\Pred, \Post
-				 } {s \OTWeakarrow {\alpha} s'} \in\WT
+				 } {s \OTWeakarrow {\alpha'} s'} \in\WT
 %}
 \end{mathpar}
-\TODO{changer alpha...}
+\TODO{changer alpha...}\\
 where\\
 $
-s=s^1_0 \wedge s^1_{n+1}=s_0^2 \wedge s_1^2 = s^3_0 \wedge s^3_{m+1}=s',\\
+\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n}^{0}\Post_j^1}}\\
+s=s^1_0 \wedge s^1_{n+1}=s_0^2 \wedge s_1^2 = s^3_0 \wedge s^3_{m+1}=s'\\
 \displaystyle{
@@
 		\Pred, \Post
-				 } {s' \OTWeakarrow {\alpha} s''} \in\WT
+				 } {s' \OTWeakarrow {\alpha'} s''} \in\WT
 }
@@
 \\
-\Pred\,''=\Pred\,'\land\Pred\subst{\Post\,'}%\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
-}
-{
-\openrule
-         {
-          \vis{\set{\beta}} \dotcup \set{\gamma},
-		\Pred\,'',\Id(s'')
-				 } 
-         {s \OTWeakarrow {\alpha} s''} \in\WT
+\set{\gamma''}= \vis{\set{\beta}} \dotcup \set{\gamma}\subst{\Post\,'}\quad
+\Pred\,''=\Pred\,'\land\Pred\subst{\Post\,'}\\%\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
+\Post\,''=\Id(s'')\shortotimes\Post\shortotimes\Post\,' \quad \alpha''=\alpha'\subst{\Post\,'}
+}
+{
+\openrule
+         {
+          \set{\gamma''}, \Pred\,'',\Post\,''
+				 } 
+         {s \OTWeakarrow {\alpha''} s''} \in\WT
 } \WTTrois
@@
      \land \alpha\!=\!\alpha_x \land  
-     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)}$
+     \Pred_{s',t_x}\subst{\Post_{OT}\shortotimes\Post_{OT_x}}\right)}$
 
@@
      \land \alpha\!=\!\alpha_x\land  
-     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\big)$\\
+     \Pred_{s',t_x}\subst{\Post_{OT}\shortotimes\Post_{OT_x}}\big)$\\
 and  suppose the following statement holds:
@@
      \land \alpha_x\!=\!\tau \land  
-     \Pred_{s_1^1,t_x}\subst{\Post^1}\subst{\Post_{OT_x}}\right)$
+     \Pred_{s_1^1,t_x}\subst{\Post^1\shortotimes\Post_{OT_x}}\right)$
 
@@
  \!\!  \left( \forall j\in J_{x y}. \vis{\beta^2_j}\!=\!\gamma_{jx y}\Rightarrow \Pred_{OT_{x y}}\!\land \alpha\!=\!\alpha_{x y} \land  
-     \Pred_{s_1^2,t_{x y}}\subst{\Post^2}\subst{\Post_{OT_{x y}}}\right)$
+     \Pred_{s_1^2,t_{x y}}\subst{\Post^2\shortotimes\Post_{OT_{x y}}}\right)$
 
@@
      \land\! \alpha_{x y z}\!=\!\tau \land  
-     \Pred_{s^3_1,t_{x y z}}\subst{\Post^3}\subst{\Post_{OT_{x y z}}}\right)$
+     \Pred_{s^3_1,t_{x y z}}\subst{\Post^3\shortotimes\Post_{OT_{x y z}}}\right)$
 
@@
 \\
-\Pred=\Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}}\land (\Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}})\subst{\Post_{OT_x}}
+\Pred=\Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}}\land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}
 }
@@
            \gamma_{j x}^{j\in J_{x}} \dotcup \gamma_{j x y}^{j\in J_{x y}}\dotcup\gamma_{j x y z}^{j\in J_{x y z}},
-		\Pred, \Post_{OT_{x y z}}\subst {\Post_{OT_{x y}}}\subst{\Post_{OT_{x}}}}  
+		\Pred, \Post_{OT_{x y z}}\subst {\Post_{OT_{x y}}\shortotimes\Post_{OT_{x}}}}  
          {t \OTWeakarrow {\alpha_{x y}} t_{x y z}} 
@@
 \vis{\beta^3_j}\!\!=\!\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\!\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \land \alpha_x\!=\!
-\tau \!\land \alpha\!=\!\alpha_{x y} \land \alpha_{x y z}\!=\!\tau \land \Pred_{s^3_1,t_{x y z}}  \subst{\underbrace{\Post^3\shortotimes\Post^2\shortotimes\Post^1}_{\Post_{OT}}\shortotimes \Post_{OT_{x y z}}\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$
+\tau \!\land \alpha\!=\!\alpha_{x y} \land \alpha_{x y z}\!=\!\tau \land \Pred_{s^3_1,t_{x y z}}  \subst{\underbrace{\Post^3\shortotimes\Post^2\shortotimes\Post^1}_{\Post_{OT}}\,\shortotimes \Post_{OT_{x y z}}\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$
 Therefore, having $s^3_1=s'$ we can conclude:\\

### 2019-04-30 2016-Weak-FH-Bisim/WeakBisim.tex
Huge pass on lemma 4

@@
 
-We use ${\displaystyle \bigotimes_{i=n}^{0} \Post_i}$ to denote  $\Post_n\otimes .. \otimes \Post_0$. By convention ${\displaystyle \bigotimes_{i=-1}^{0} \Post_i}$ is the identity.
+We use ${\displaystyle \bigotimes_{i=n}^{0} \Post_i}$ to denote  $\Post_n\otimes ..
+\otimes \Post_0$.
+By convention ${\displaystyle \bigotimes_{i=-1}^{0} \Post_i}$ is the identity.
+Note that for any term $t$ we have: $t\subst{\Post\shortotimes\Post'} = t\subst{\Post}\subst{\Post'}$
 
@@
 \end{mathpar}
-\TODO{changer alpha...}\\
 where\\
@@
 
-\begin{proof} ($\Rightarrow$) We proceed by induction on  $l=n+m+1$, which is in fact the number of transitions with which we  build  a weak transition (introduced in Definition \ref{def:buildweakOT}).
+\begin{proof} ($\Rightarrow$) We proceed by induction on  $n$ and $m$ (where between each step either $m$ or $n$ increases).
 \begin{itemize}
-\item The base case $l=1$, so $n=0$ and $m=0$, we have:
+\item The base case there is one transition, so $n=0$ and $m=0$, we have:
 \begin{mathpar}
@@
 \end{mathpar} 
-\item For the inductive step, first we have by induction hypothesis that the formula holds for some length $l$.
-Induction step is to infer that formula holds for transitions of length $l + 1$.
-As the condition holds for $l$, it means that there is $n$  $m$, $n'$,$m'$ such that $l=n+m+1$, and $l+1=n'+m'+1$ and either $n'=n+1$ or $m'=m+1$ (exclusively).
-\LUDO{je trouve toujours ca pas tres correct le coup $l=n+m+1$ donc $l'=(n+1)+m+1$ ou $l'=n+(m+1)+1$ mais bon comme on dirait que ma proposition plait pas, on verra a la review}
-We consider the case $n'=n+1$, and $m'=m+1$ are similar.
-Side conditions are omitted for readability.
-We first focus on the left part of the disjunction.
-Let us consider the sequence of ($n+m+1$) open transitions:
-\begin{mathpar}
-\Big(\forall i \in [0..n].\openrule
+\item For the inductive step, first we have by induction hypothesis that the formula holds for some lengths $m$ and $n$.
+Induction step is to infer that formula holds for transitions of length $m+1$ or $n+1$.
+We consider the case $n'=n+1$ (because $m'=m+1$ is similar).  We first focus on the left part of the disjunction. Let us consider the sequence of ($n+m+1$) open transitions:
+\begin{mathpar}
+\Big(\forall i \in [0..n+1].\openrule
     {
@@
          {
-           \set{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
+           \set{\beta^3_i},\Pred^3_i,\Post_{i 3}   }
          {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
@@
 
-By recurrence hypothesis we suppose that the statement holds for some  set of open transitions of length $l$. In particular, we have:\\
+By recurrence hypothesis we suppose that the statement holds for $n$ and $m$ (we remove the first tau transition). We have:\\
 
@@
 %\inferrule 
-\Big(\forall i \in [0..n].\openrule
+\Big(\forall i \in [1..n+1].\openrule
     {
@@
          {
-           \set{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
+           \set{\beta^3_i},\Pred^3_i,\Post_{i 3}   }
          {s^3_i \OTarrow {\tau} s^3_{i+1}}\! \in\! \mathcal{T}
@@
 		\Pred, \Post
-				 } {s' \OTWeakarrow {\alpha'} s''} \in\WT
-}
+				 } {s'' \OTWeakarrow {\alpha'} s'} \in\WT
+}
+$
+where\\
+$
+\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\Post_j^1}}\\
+s''=s^1_0 \wedge s^1_{n+2}=s_0^2 \wedge s_1^2 = s^3_0 \wedge s^3_{m+1}=s'\\
+\displaystyle{
+\set{\gamma}=\mybigdotcup_{i=1}^{n+1} \vis{\set{\beta^1_i}\subst{\bigotimes_{j=i-1}^{1} \Post_j^1 } }  \dotcup  \vis{\set{\beta^2}\subst{\bigotimes_{j=n+1}^{1}\Post_j^1}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i} \subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j} }}
+\\
+\Pred=\bigwedge_{i=1}^{n+1}\Pred^1_i\subst{\bigotimes_{j=i-1}^{1}\Post_j^1}\land\Pred^2 \subst{\bigotimes_{j={n+1}}^{1}\Post_j^1}\land\\ 
+~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_i^3\subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j={n+1}}^{1}\Post^1_j}\Big)\\
+\Post=\bigotimes_{j=m}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j={n+1}}^{1}\Post^1_j
 $
@@
          {
-           \set{\beta},\Pred\,',\Post\,'}
-         {s \OTarrow {\tau} s'} \in \mathcal{T}
-%}
+           \set{\beta_{0}^{1}},\Pred_0^1,\Post_0^1}
+         {s_0^1 \OTarrow {\tau} s_1^1} \in \mathcal{T}%}
 \end{mathpar}
@@
          {
-           \set{\beta},\Pred\,',\Post\,'}
-         {s \OTarrow {\tau} s'} \in \mathcal{T}
+           \set{\beta_{0}^{1}},\Pred_0^1,\Post_0^1}
+         {s_0^1 \OTarrow {\tau} s_1^1} \in \mathcal{T}
 \implies 
@@
        {
-           \vis{\set{\beta}}\!,\Pred\,',\Post\,'
-				 } {s \OTWeakarrow {\tau} s'} \in \WT
+           \vis{\set{\beta_{0}^{1}}}\!,\Pred_0^1,\Post_0^1
+				 } {s_0^1 \OTWeakarrow {\tau}s_1^1} \in \WT
 }
@@
          {
-          \emptyset,\True,\Id(s'')
-				 } {s'' \OTWeakarrow {\tau} s''} \in \WT
+          \emptyset,\True,\Id(s')
+				 } {s' \OTWeakarrow {\tau} s'} \in \WT
 \end{mathpar}
@@
        {
-           \vis{\set{\beta}},\Pred\,',\Post\,'   }
-         {s \OTWeakarrow {\tau} s'} \in \WT
+           \vis{\set{\beta_{0}^{1}}}\!,\Pred_0^1,\Post_0^1
+				 } {s_0^1 \OTWeakarrow {\tau}s_1^1} \in \WT
 \qquad
@@
 		\Pred, \Post
-				 } {s' \OTWeakarrow {\alpha} s''} \in\WT
+				 } {s'' \OTWeakarrow {\alpha} s'} \in\WT
 \qquad
@@
           \emptyset,\True,\Id(s'')
-				 } {s'' \OTWeakarrow {\tau} s''} \in \WT
+				 } {s' \OTWeakarrow {\tau} s'} \in \WT
 \\
-\set{\gamma''}= \vis{\set{\beta}} \dotcup \set{\gamma}\subst{\Post\,'}\quad
-\Pred\,''=\Pred\,'\land\Pred\subst{\Post\,'}\\%\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
-\Post\,''=\Id(s'')\shortotimes\Post\shortotimes\Post\,' \quad \alpha''=\alpha'\subst{\Post\,'}
+\set{\gamma''}= \vis{\set{\beta_{0}^{1}}} \dotcup \set{\gamma}\subst{\Post_0^1}\quad
+\Pred\,''=\Pred_0^1\land\Pred\subst{\Post_0^1}\\%\land (\Pred_3\subst{\Post_2})\subst{\Post_0^1}
+\Post\,''=\Id(s'')\shortotimes\Post\shortotimes\Post_0^1 \quad \alpha''=\alpha'\subst{\Post_0^1}
 }
@@
 				 } 
-         {s \OTWeakarrow {\alpha''} s''} \in\WT
+         {s_0^1 \OTWeakarrow {\alpha''} s'} \in\WT
 } \WTTrois
 \end{mathpar}
+where we obtain the conclusion of the lemma, as required with the following assertions (derived from previous assertions):\\
+$
+\alpha''=\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\Post_j^1}}\subst{\Post_0^1} = \alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{0}\Post_j^1}}\\
+s^1_0=s^1_0 \wedge s^1_{n+2}=s_0^2 \wedge s_1^2 = s^3_0 \wedge s^3_{m+1}=s'\\
+\displaystyle{
+\set{\gamma''}=\mybigdotcup_{i=0}^{n+1} \vis{\set{\beta^1_i}\subst{\bigotimes_{j=i-1}^{1} \Post_j^1 } }  \dotcup  \vis{\set{\beta^2}\subst{\bigotimes_{j=n+1}^{1}\Post_j^1}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i} \subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j} }}
+\\
+\Pred=\bigwedge_{i=0}^{n+1}\Pred^1_i\subst{\bigotimes_{j=i-1}^{0}\Post_j^1}\land\Pred^2 \subst{\bigotimes_{j={n+1}}^{0}\Post_j^1}\land\\ 
+~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_i^3\subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j={n+1}}^{0}\Post^1_j}\Big)\\
+\Post=\bigotimes_{j=m}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j={n+1}}^{0}\Post^1_j
+$
 
@@
          {
-           \set{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
+           \set{\gamma_3},\Pred_3,\Post_3    }
          {s'' \OTWeakarrow {\tau} s'''} \in\WT
 \\
-\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
-}
-{
-\openrule
-         {
-           \set{\gamma_1}\dotcup \set{\gamma_2}\dotcup\set{\gamma_3},
+\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land \Pred_3\subst{\Post_2\shortotimes\Post_1}
+\\
+\set{\gamma}=\set{\gamma_1}\dotcup \set{\gamma_2}\subst{\Post_1}\dotcup\set{\gamma_3}\subst{\Post_2\shortotimes \Post_1}\\
+\alpha'=\alpha\subst{\Post_1}
+}
+{
+\openrule
+         {
+           \set{\gamma},
 		\Pred,
-				({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K} } 
-         {s \OTWeakarrow {\alpha} s'''} \in\WT
+				\Post_3\shortotimes{\Post_2}\shortotimes{\Post_1} }
+         {s \OTWeakarrow {\alpha'} s'''} \in\WT
 }
@@
 s=s_{10} \wedge s_{1{(n_1+1)}}\!=s',
-\displaystyle{\set{\gamma_1}=\mybigdotcup_{i=0}^{n_1} \vis{\set{\beta_{1i}}}}, 
-\Pred_1\!=\!\bigwedge_{i=0}^{n_1}\Pred_{1i}, \Post_1= \bigotimes_{i=0}^{n_1} \subst{\Post_{1i}}\\
+\displaystyle{\set{\gamma_1}= \mybigdotcup_{i=0}^{n_1} \vis{\set{\beta_{1 i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1 j} } }} \\
+\Pred_1\!=\!\bigwedge_{i=0}^{n_1}(\Pred_{1i} \subst{\bigotimes_{j=i-1}^{0}\Post_{i j}} ), \Post_1= \bigotimes_{i=0}^{n_1} \subst{\Post_{1i}} 
 $
-\TODO{$\Post_1= \biguplus_{i=0}^{n_1} \Post_{1i}$ or bigotimes?}
+
 \item Similarly, a series of $m_1$ open transitions such that $m_1=n+m+1$   can be simplified as follows: 
@@
 $ 
-s''\!=\!s_{30} \wedge s_{3(m_1+1)}\!=\!s''',
-\displaystyle{\set{\gamma_3}\!=\!\mybigdotcup_{i=0}^{m_1}\vis{\set{\beta_{3i}}}},
-\Pred_3\!=\!\bigwedge_{i=0}^{m_1}\Pred_{3i},\Post_3\!=\!\bigotimes_{i=0}^{m_1} \subst{\Post_{3i}}\\
+s''=s_{30} \wedge s_{3{(m_1+1)}}\!=s''',
+\displaystyle{\set{\gamma_3}= \mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{3 i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{3 j} } }} \\
+\Pred_3\!=\!\bigwedge_{i=0}^{m_1}(\Pred_{3i} \subst{\bigotimes_{j=i-1}^{0}\Post_{3 j}} ), \Post_1= \bigotimes_{i=0}^{m_1} \subst{\Post_{3i}} 
 $
@@
            \set{\gamma_2},\Pred_2,\Post_2  }
-         {s' \OTWeakarrow {\alpha} s''} \in\! \WT
+         {s' \OTWeakarrow {\alpha'} s''} \in\! \WT
 \implies 
@@
            \set{\beta'},\Pred\,',\Post\,' }
-         {s_2 \OTarrow {\alpha} s_2'} \in \mathcal{T}
+         {s_2 \OTarrow {\alpha''} s_2'} \in \mathcal{T}
  \wedge
@@
          {
-           \set{\beta_{2i}'},\Pred_{2i}^{\,\prime},({x_k\gets e_k})^{k\in K}    }
+           \set{\beta_{2i}'},\Pred_{2i}^{\,\prime},\Post'_{2i}    }
          {s_{2i}' \OTarrow {\tau} s_{2(i+1)}'} \in \mathcal{T}
@@
 $
+\alpha''=\alpha'\displaystyle{\subst{\bigotimes_{j=n_2}^{0}\Post_{2j}}}\\
 s'=s_{20} \wedge s_{2(n_2+1)}=s_2 \wedge  s_2' = s_{20}' \wedge s_{2(m_2+1)}'=s''\\
-\displaystyle{\set{\gamma_2}=\mybigdotcup_{i=0}^{n_2} \vis{\set{\beta_{2i}}} \dotcup  \vis{\set{\beta'}}  \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{2i}'}}}
+\displaystyle{
+\set{\gamma_2}=\mybigdotcup_{i=0}^{n_2} \vis{\set{\beta_{2i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{2 j} } }  \dotcup  \vis{\set{\beta'}\subst{\bigotimes_{j=n}^{0}\Post_j^1}} }\\~\qquad
+\dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{2i}} \subst{\bigotimes_{j=i-1}^{0}\Post'_{2j}\shortotimes\Post'\shortotimes\bigotimes_{j=n}^{0}\Post_{2j}} }
 \\
-\Pred_2=\bigwedge_{i=0}^{n_2}\Pred_{2i}\land\Pred\,'\bigotimes_{i=0}^{n_2}\subst{\Post_{2i}}\land \big(\bigwedge_{i=0}^{m_2}\Pred_{2i}^{\,\prime}\subst{\Post\,'}\big)\bigotimes_{i=0}^{n_1}\subst{\Post_{2i}}
-\\
-\Post_2= \big({x_k\gets e_k\subst {\Post\,'}\bigotimes_{i=0}^{n_2}\subst{\Post_{2i}}}\big)^{k\in K}
+\Pred_2=\bigwedge_{i=0}^{n_2}\Pred_{2i}\subst{\bigotimes_{j=i-1}^{0}\Post_{2j}}\land\Pred' \subst{\bigotimes_{j={n_2}}^{0}\Post_{2j}}\land\\ 
+~\qquad\quad\Big(\bigwedge_{i=0}^{m_2}\Pred_i^3\subst{\bigotimes_{j=i-1}^{0}\Post'_{2j}\shortotimes\Post'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}}\Big)\\
+\Post_2=\bigotimes_{j=m_2}^{0}\Post'_{2j}\shortotimes\Post'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}
 $
+
 \end{enumerate}
@@
     {
-       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
-         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in\mathcal{T} \wedge
-
-\openrule
-         {
-           \set{\beta^2},\Pred^2,\Post^2 }
-         {s_0^2 \OTarrow {\alpha} s_1^2} \in \mathcal{T}
+       \set{\beta_{4i}},\Pred_{4i},\Post_{4i}   }
+         {s_{4i} \OTarrow {\tau} s_{4(i+1)}} \in\mathcal{T} \wedge
+
+\openrule
+         {
+           \set{\beta'},\Pred\,',\Post\,' }
+         {s_2 \OTarrow {\alpha''} s_2'} \in \mathcal{T}
 \wedge\,
 \forall i \in [0..(m_1\!+\!m_2)].\openrule
-         {\set{\beta^3_i},\Pred^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
-         {s^3_i\OTarrow {\tau} s^3_{i+1}}\in\mathcal{T}\bigg)  
+         {\set{\beta_{5i}},\Pred_{5 i},\Post_{5i}    }
+         {s_{5i}\OTarrow {\tau} s_{5({i+1})}}\in\mathcal{T}\bigg)  
 \end{mathpar}
@@
 such that\\
+
 $
-s_i^1= \left\{
+s_{4i}= \left\{
  \begin{array}{ll}
@@
 \end{array}
-\right. \quad \wedge \quad
-s_i^3= \left\{
+\right.  \qquad \qquad
+s_{5i}= \left\{
  \begin{array}{ll}
@@
 \right. \\
+$
+\\
+
+ and similarly for $Pred_{4i}$, $Pred_{5i}$, $Pred_{4i}$, and $Pred_{4i}$  \TODO{define or OK this way?}
+
+We have the following assertions:\\
+$
+{\displaystyle \alpha''=\alpha\subst{\bigotimes_{j=n_1+n_2}^{0}\Post_{4j}}}\\
+s\!=\!s_{40} \wedge s_{4(n_1+n_2+1)}\!=s_2 \wedge s_2' = s_{50} \wedge s_{5(m_1+m_2+1)}\!=\!s'\\
 ~~\\
-s\!=\!s^1_0 \wedge s^1_{(n_1+n_2+1)}\!=s_0^2 \wedge s_1^2 = s^3_0 \wedge s^3_{(m_1+m_2+1)}\!=\!s'''\\
-~~\\
-\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2}\!\! \vis{\set{\beta^1_i}}
-\dotcup\vis{\set{\beta^2}}\dotcup\!\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta^3_i}}
-}\\
-\displaystyle{\Pred=\bigwedge_{i=0}^{n_2}\Pred^1_i\land\Pred^2\bigotimes_{i=0}^{n_2}\subst{\Post^1_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred^1_i\subst{\Post^2}\Big)\bigotimes_{i=0}^{n_1}\subst{\Post^1_i}}
+\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2} \vis{\set{\beta_{4i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{4 j} } }  \dotcup  \vis{\set{\beta'}\subst{\bigotimes_{j=n_1+n_2}^{0}\Post_{4j}}}}\\~\qquad
+\dotcup\!\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta_{5i}}\subst{\bigotimes_{j=i-1}^{0}\Post'_{5i}\shortotimes\Post'\shortotimes\bigotimes_{j=n_1+n_2}^{0}\Post_{4i}} }
 \\
-\displaystyle{\Post= \big({x^3_k\gets e^3_k\subst {\Post^2}\bigotimes_{i=0}^{n_2}\subst{\Post^1_i}}\big)^{k\in K}}
+\displaystyle{\Pred=
+\bigwedge_{i=0}^{n_1+n_2}\Pred_{4i}\subst{\bigotimes_{j=i-1}^{0}\Post_{4j}}\land\Pred' \subst{\bigotimes_{j={n_1+n_2}}^{0}\Post_{4j}}\land}\\ 
+~\qquad\quad\Big(\bigwedge_{i=0}^{m_1+m_2}\Pred_{5i}\subst{\bigotimes_{j=i-1}^{0}\Post_{5j}\shortotimes\Post'\shortotimes\bigotimes_{j={n_1+n_2}}^{0}\Post_{4j}}\Big)\\
+\Post=\bigotimes_{j=m_1+m_2}^{0}\Post_{5j}\shortotimes\Post'\shortotimes\bigotimes_{j={n_1+n_2}}^{0}\Post_{4j}
 $\\
-This concludes the inductive step, showing  that the decomposition expressed by the $\Leftarrow$ direction of the lemma is always possible. \qed
+This concludes the inductive step, showing  that the decomposition expressed by the $\Leftarrow$ direction of the lemma is always possible with the right side conditions. \qed
 \end{itemize}
@@
 \end{mathpar}
-By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
+By Lemma \ref{lem-rel-OT-WOT} this implies the following \TODO{replace $\alpha$ by $\alpha'$}: \\			
 $ \forall p\! \in [0..m_1]\,		

### 2019-05-02 2016-Weak-FH-Bisim/WeakBisim.tex
change notations in lemma 4
notations suite

@@
 \alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'$; or \\ 
-there exist   $\set{\beta^1}_i$, $\set{\beta^2_i}$, and $\set{\beta^3_i}$, $\Pred^1_i$, $\Pred^3_i$, $\Post^1_i$, and  $\Pred^2$, $\Post^2$ s.t.:
+there exist   $\set{\beta_{1i}}$, $\set{\beta_{2i}}$, and $\set{\beta_{3i}}$, $\Pred_{1i}$, $\Pred_{3i}$, $\Post_{1i}$, and  $\Pred_2$, $\Post_2$ s.t.:
 \begin{mathpar}
@@
     {
-       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
-         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \quad \wedge
+       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
+         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T} \quad \wedge
 \quad
@@
          {
-           \set{\beta^2},\Pred^2,\Post^2 }
-         {s_0^2 \OTarrow {\alpha} s_1^2} \in \mathcal{T}
+           \set{\beta_2},\Pred_2,\Post_2 }
+         {s_2 \OTarrow {\alpha} s'_2} \in \mathcal{T}
 \quad \wedge\\
@@
          {
-           \set{\beta^3_i},\Pred^3_i,\Post_i^3    }
-         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
+           \set{\beta_{3i}},\Pred_{3i},\Post_{3i}    }
+         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}
  \end{mathpar}
@@
 \alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n}^{0}\Post_j^1}}\\
-s=s^1_0 \wedge s^1_{n+1}=s_0^2 \wedge s_1^2 = s^3_0 \wedge s^3_{m+1}=s'\\
+s=s_{10} \wedge s_{1(n+1)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
 \displaystyle{
-\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}\subst{\bigotimes_{j=i-1}^{0} \Post_j^1 } }  \dotcup  \vis{\set{\beta^2}\subst{\bigotimes_{j=n}^{0}\Post_j^1}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i} \subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j} }}
+\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
 \\
-\Pred=\bigwedge_{i=0}^n\Pred^1_i\subst{\bigotimes_{j=i-1}^{0}\Post_j^1}\land\Pred^2 \subst{\bigotimes_{j=n}^{0}\Post_j^1}\land\\ 
-~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_i^3\subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j}\Big)\\
-\Post=\bigotimes_{j=m}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j
+\Pred=\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=n}^{0}\Post_{1j}}\land\\ 
+~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}}\Big)\\
+\Post=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}
 $
@@
 Induction step is to infer that formula holds for transitions of length $m+1$ or $n+1$.
-We consider the case $n'=n+1$ (because $m'=m+1$ is similar).  We first focus on the left part of the disjunction. Let us consider the sequence of ($n+m+1$) open transitions:
+We consider the case $n'=n+1$ (because $m'=m+1$ is similar).
+We first focus on the left part of the disjunction.
+Let us consider the sequence of ($n+m+1$) open transitions: \TODO{sur cette page coorection non faite}
 \begin{mathpar}
@@
          {
-           \set{\beta^3_i},\Pred^3_i,\Post_{i 3}   }
-         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
+           \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
+         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}
 \Big) 
@@
     {
-       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
-         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T} \,\wedge\,
-\openrule
-         {
-           \set{\beta^2},\Pred^2,\Post^2 }
-         {s_0^2 \OTarrow {\alpha} s_1^2} \in \mathcal{T}
+       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
+         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T} \,\wedge\,
+\openrule
+         {
+           \set{\beta_2},\Pred_2,\Post_2 }
+         {s_2 \OTarrow {\alpha} s'_2} \in \mathcal{T}
 \, \wedge\\
@@
          {
-           \set{\beta^3_i},\Pred^3_i,\Post_{i 3}   }
-         {s^3_i \OTarrow {\tau} s^3_{i+1}}\! \in\! \mathcal{T}
+           \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
+         {s_{3i} \OTarrow {\tau} s_{3(i+1)}}\! \in\! \mathcal{T}
 \Big) \\       
@@
 \alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\Post_j^1}}\\
-s''=s^1_0 \wedge s^1_{n+2}=s_0^2 \wedge s_1^2 = s^3_0 \wedge s^3_{m+1}=s'\\
+s''=s_{10} \wedge s_{1(n+2)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
 \displaystyle{
-\set{\gamma}=\mybigdotcup_{i=1}^{n+1} \vis{\set{\beta^1_i}\subst{\bigotimes_{j=i-1}^{1} \Post_j^1 } }  \dotcup  \vis{\set{\beta^2}\subst{\bigotimes_{j=n+1}^{1}\Post_j^1}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i} \subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j} }}
+\set{\gamma}=\mybigdotcup_{i=1}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
 \\
-\Pred=\bigwedge_{i=1}^{n+1}\Pred^1_i\subst{\bigotimes_{j=i-1}^{1}\Post_j^1}\land\Pred^2 \subst{\bigotimes_{j={n+1}}^{1}\Post_j^1}\land\\ 
-~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_i^3\subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j={n+1}}^{1}\Post^1_j}\Big)\\
-\Post=\bigotimes_{j=m}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j={n+1}}^{1}\Post^1_j
+\Pred=\bigwedge_{i=1}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{1}\Post_{1j}}\land\\ 
+~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}}\Big)\\
+\Post=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}
 $
@@
          {
-           \set{\beta_{0}^{1}},\Pred_0^1,\Post_0^1}
-         {s_0^1 \OTarrow {\tau} s_1^1} \in \mathcal{T}%}
+           \set{\beta_{10}},\Pred_{10},\Post_{10}}
+         {s_{10} \OTarrow {\tau} s_{11}} \in \mathcal{T}%}
 \end{mathpar}
@@
          {
-           \set{\beta_{0}^{1}},\Pred_0^1,\Post_0^1}
-         {s_0^1 \OTarrow {\tau} s_1^1} \in \mathcal{T}
+           \set{\beta_{10}},\Pred_{10},\Post_{10}}
+         {s_{10} \OTarrow {\tau} s_{11}} \in \mathcal{T}
 \implies 
@@
        {
-           \vis{\set{\beta_{0}^{1}}}\!,\Pred_0^1,\Post_0^1
-				 } {s_0^1 \OTWeakarrow {\tau}s_1^1} \in \WT
-}
-\end{mathpar}
-
-On the other hand, by rule (\WTUn) we can write the following weak open transition:
+           \vis{\set{\beta_{10}}}\!,\Pred_{10},\Post_{10}
+				 } {s_{10} \OTWeakarrow {\tau}s_{11}} \in \WT
+}
+\end{mathpar}
+
+On the other hand, by rule (\WTUn) we have the following weak open transition:
 \begin{mathpar}
@@
        {
-           \vis{\set{\beta_{0}^{1}}}\!,\Pred_0^1,\Post_0^1
-				 } {s_0^1 \OTWeakarrow {\tau}s_1^1} \in \WT
+           \vis{\set{\beta_{10}}}\!,\Pred_{10},\Post_{10}
+				 } {s_{10} \OTWeakarrow {\tau}s_{11}} \in \WT
 \qquad
@@
 		\Pred, \Post
-				 } {s'' \OTWeakarrow {\alpha} s'} \in\WT
+				 } {s'' \OTWeakarrow {\alpha'} s'} \in\WT
 \qquad
@@
 \\
-\set{\gamma''}= \vis{\set{\beta_{0}^{1}}} \dotcup \set{\gamma}\subst{\Post_0^1}\quad
-\Pred\,''=\Pred_0^1\land\Pred\subst{\Post_0^1}\\%\land (\Pred_3\subst{\Post_2})\subst{\Post_0^1}
-\Post\,''=\Id(s'')\shortotimes\Post\shortotimes\Post_0^1 \quad \alpha''=\alpha'\subst{\Post_0^1}
+\set{\gamma''}= \vis{\set{\beta_{10}}} \dotcup \set{\gamma}\subst{\Post_{10}}\quad
+\Pred\,''=\Pred_{10}\land\Pred\subst{\Post_{10}}\\%\land (\Pred_3\subst{\Post_2})\subst{\Post_{10}}
+\Post\,''=\Id(s'')\shortotimes\Post\shortotimes\Post_{10} \quad \alpha''=\alpha'\subst{\Post_{10}}
 }
@@
 				 } 
-         {s_0^1 \OTWeakarrow {\alpha''} s'} \in\WT
+         {s_{10} \OTWeakarrow {\alpha''} s'} \in\WT
 } \WTTrois
@@
 $
-\alpha''=\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\Post_j^1}}\subst{\Post_0^1} = \alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{0}\Post_j^1}}\\
-s^1_0=s^1_0 \wedge s^1_{n+2}=s_0^2 \wedge s_1^2 = s^3_0 \wedge s^3_{m+1}=s'\\
+\alpha''=\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}}\subst{\Post_{10}} = \alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{0}\Post_{1j}}}\\
+s_{10}=s_{10} \wedge s_{1(n+2)}=s_{2} \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
 \displaystyle{
-\set{\gamma''}=\mybigdotcup_{i=0}^{n+1} \vis{\set{\beta^1_i}\subst{\bigotimes_{j=i-1}^{1} \Post_j^1 } }  \dotcup  \vis{\set{\beta^2}\subst{\bigotimes_{j=n+1}^{1}\Post_j^1}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i} \subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=n}^{0}\Post^1_j} }}
+\set{\gamma''}=\mybigdotcup_{i=0}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
 \\
-\Pred=\bigwedge_{i=0}^{n+1}\Pred^1_i\subst{\bigotimes_{j=i-1}^{0}\Post_j^1}\land\Pred^2 \subst{\bigotimes_{j={n+1}}^{0}\Post_j^1}\land\\ 
-~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_i^3\subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j={n+1}}^{0}\Post^1_j}\Big)\\
-\Post=\bigotimes_{j=m}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j={n+1}}^{0}\Post^1_j
+\Pred=\bigwedge_{i=0}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{0}\Post_{1j}}\land\\ 
+~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{i3}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{0}\Post_{1j}}\Big)\\
+\Post=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{0}\Post_{1j}
 $
@@
 \displaystyle{\set{\gamma_1}= \mybigdotcup_{i=0}^{n_1} \vis{\set{\beta_{1 i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1 j} } }} \\
-\Pred_1\!=\!\bigwedge_{i=0}^{n_1}(\Pred_{1i} \subst{\bigotimes_{j=i-1}^{0}\Post_{i j}} ), \Post_1= \bigotimes_{i=0}^{n_1} \subst{\Post_{1i}} 
+\Pred_1\!=\!\bigwedge_{i=0}^{n_1}(\Pred_{1i} \subst{\bigotimes_{j=i-1}^{0}\Post_{i j}} ), \Post_1= \bigotimes_{i=n_1}^{0} \subst{\Post_{1i}} 
 $
@@
 \displaystyle{\set{\gamma_3}= \mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{3 i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{3 j} } }} \\
-\Pred_3\!=\!\bigwedge_{i=0}^{m_1}(\Pred_{3i} \subst{\bigotimes_{j=i-1}^{0}\Post_{3 j}} ), \Post_1= \bigotimes_{i=0}^{m_1} \subst{\Post_{3i}} 
+\Pred_3\!=\!\bigwedge_{i=0}^{m_1}(\Pred_{3i} \subst{\bigotimes_{j=i-1}^{0}\Post_{3 j}} ), \Post_3= \bigotimes_{i=m_1}^{0} \subst{\Post_{3i}} 
 $
@@
 \displaystyle{
-\set{\gamma_2}=\mybigdotcup_{i=0}^{n_2} \vis{\set{\beta_{2i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{2 j} } }  \dotcup  \vis{\set{\beta'}\subst{\bigotimes_{j=n}^{0}\Post_j^1}} }\\~\qquad
-\dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{2i}} \subst{\bigotimes_{j=i-1}^{0}\Post'_{2j}\shortotimes\Post'\shortotimes\bigotimes_{j=n}^{0}\Post_{2j}} }
+\set{\gamma_2}=\mybigdotcup_{i=0}^{n_2} \vis{\set{\beta_{2i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{2 j} } }  \dotcup  \vis{\set{\beta'}\subst{\bigotimes_{j=n_2}^{0}\Post_{2j}}} }\\~\qquad
+\dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{2i}} \subst{\bigotimes_{j=i-1}^{0}\Post'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j=n_2}^{0}\Post_{2j}} }
 \\
-\Pred_2=\bigwedge_{i=0}^{n_2}\Pred_{2i}\subst{\bigotimes_{j=i-1}^{0}\Post_{2j}}\land\Pred' \subst{\bigotimes_{j={n_2}}^{0}\Post_{2j}}\land\\ 
-~\qquad\quad\Big(\bigwedge_{i=0}^{m_2}\Pred_i^3\subst{\bigotimes_{j=i-1}^{0}\Post'_{2j}\shortotimes\Post'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}}\Big)\\
+\Pred_2=\bigwedge_{i=0}^{n_2}\Pred_{2i}\subst{\bigotimes_{j=i-1}^{0}\Post_{2j}}\land\Pred\,' \subst{\bigotimes_{j={n_2}}^{0}\Post_{2j}}\land\\ 
+~\qquad\quad\Big(\bigwedge_{i=0}^{m_2}\Pred\,'_{2i}\subst{\bigotimes_{j=i-1}^{0}\Post'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}}\Big)\\
 \Post_2=\bigotimes_{j=m_2}^{0}\Post'_{2j}\shortotimes\Post'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}
@@
 \displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2} \vis{\set{\beta_{4i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{4 j} } }  \dotcup  \vis{\set{\beta'}\subst{\bigotimes_{j=n_1+n_2}^{0}\Post_{4j}}}}\\~\qquad
-\dotcup\!\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta_{5i}}\subst{\bigotimes_{j=i-1}^{0}\Post'_{5i}\shortotimes\Post'\shortotimes\bigotimes_{j=n_1+n_2}^{0}\Post_{4i}} }
+\dotcup\!\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta_{5i}}\subst{\bigotimes_{j=i-1}^{0}\Post'_{5i}\shortotimes\Post\,'\shortotimes\bigotimes_{j=n_1+n_2}^{0}\Post_{4i}} }
 \\
 \displaystyle{\Pred=
-\bigwedge_{i=0}^{n_1+n_2}\Pred_{4i}\subst{\bigotimes_{j=i-1}^{0}\Post_{4j}}\land\Pred' \subst{\bigotimes_{j={n_1+n_2}}^{0}\Post_{4j}}\land}\\ 
-~\qquad\quad\Big(\bigwedge_{i=0}^{m_1+m_2}\Pred_{5i}\subst{\bigotimes_{j=i-1}^{0}\Post_{5j}\shortotimes\Post'\shortotimes\bigotimes_{j={n_1+n_2}}^{0}\Post_{4j}}\Big)\\
-\Post=\bigotimes_{j=m_1+m_2}^{0}\Post_{5j}\shortotimes\Post'\shortotimes\bigotimes_{j={n_1+n_2}}^{0}\Post_{4j}
+\bigwedge_{i=0}^{n_1+n_2}\!\!\Pred_{4i}\subst{\bigotimes_{j=i-1}^{0}\Post_{4j}}\land\Pred\,' \subst{\bigotimes_{j={n_1+n_2}}^{0}\Post_{4j}}\land}\\ 
+~\qquad\quad\Big(\bigwedge_{i=0}^{m_1+m_2}\Pred_{5i}\subst{\bigotimes_{j=i-1}^{0}\Post_{5j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_1+n_2}}^{0}\Post_{4j}}\Big)\\
+\Post=\bigotimes_{j=m_1+m_2}^{0}\!\!\Post_{5j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_1+n_2}}^{0}\Post_{4j}
 $\\
@@
          \implies
-\bigg(\forall i \in [0\ldots n].\openrule
-    {
-       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
-         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}  \wedge
-
-\openrule
-         {
-           {(\beta_j^2)}^{j\in J_2},\Pred\,^2,\Post^2 }
-         {s_0^2 \OTarrow {\alpha} s_1^2} \in \mathcal{T}
+\bigg(\forall i \in [0..n].\openrule
+    {
+       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
+         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T}  \wedge
+
+\openrule
+         {
+           \set{\beta_2},\Pred_2,\Post_2 }
+         {s_{20} \OTarrow {\alpha} s_{21}} \in \mathcal{T}
  \wedge
-\forall i \in [0\ldots m].\openrule
-         {
-           \set{\beta^3_i},\Pred\,^3_i,  \Post^3_i  }
-         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
+\forall i \in [0..m].\openrule
+         {
+           \set{\beta_{3i}},\Pred_{3i},  \Post_{3i}  }
+         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}
 \bigg)
@@
 $
-s=s^1_0 \wedge s^1_n=s^2 \wedge s'^2 = s^3_0 \wedge s^3_m=s',
-\displaystyle{\gamma_j^{j\in J}=\vis{\beta_j^{j\in J}}=\mybigdotcup_{i=0}^n \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta^3_i}}}
+s=s_{10} \wedge s_{1(n+1)}=s_{20} \wedge s_{21} = s_{30} \wedge s_{3(m+1)}=s'\\
+\displaystyle{
+\gamma_j^{j\in J}=\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
 \\
-\Pred_{OT}=\bigwedge_{i=0}^n\Pred^1_i\land\Pred\,^2\bigotimes_{i=0}^{n}\subst{\Post_i^1}\land \bigwedge_{i=0}^m\Pred_i^3\subst{\Post^2}\bigotimes_{i=0}^{n}\subst{\Post^1_i}\\
-\Post_{OT}=\biguplus_{i=0}^{m}(\Post_i^3\subst{\Post^2})\bigotimes_{i=0}^{n}\subst{\Post^1_i}
-$
+\Pred_{OT}=\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=n}^{0}\Post_{1j}}\land\\ 
+~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}}\Big)\\
+\Post_{OT}=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}$
 
@@
     {
-       \set{\beta^1},\Pred^1,\Post^1   }
-         {s_0^1 \OTarrow {\tau} s_1^1} \in \mathcal{T}          
-\end{mathpar}
-we have $(s,t|\Pred_{s,t})\in\mathcal{R}$, hence $(s_0^1,t|\Pred_{s_0^1,t})\in\mathcal{R}$, since $s=s_0^1$.
+       \set{\beta_{10}},\Pred_{10},\Post_{10}   }
+         {s_{10} \OTarrow {\tau} s_{11}} \in \mathcal{T}          
+\end{mathpar}
+we have $(s,t|\Pred_{s,t})\in\mathcal{R}$, hence $(s_{10},t|\Pred_{s_{10},t})\in\mathcal{R}$, since $s=s_{10}$.
 By  Definition \ref{def-Weak-bisim} we  can deduce there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
@@
 \end{mathpar}
- such that  $\forall x,J_{x}=\{j\in J_1|\beta^1_j\neq\tau\}, (s_1^1,t_x|\Pred_{s_1^1,t_x})\in \mathcal{R}$. \\
+ such that  $\forall x,J_{x}=\{j\in J|\beta_{1j}\neq\tau\}, (s_{11},t_x|\Pred_{s_{11},t_x})\in \mathcal{R}$. \\
  $\Pred_{s,t} \land \Pred^1\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
-  \!\! \left( \forall j\in J_x.\vis{\beta^1_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
+  \!\! \left( \forall j\in J_x.\vis{\beta_{1j}}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
      \land \alpha_x\!=\!\tau \land  
-     \Pred_{s_1^1,t_x}\subst{\Post^1\shortotimes\Post_{OT_x}}\right)$
+     \Pred_{s_{11},t_x}\subst{\Post_1\shortotimes\Post_{OT_x}}\right)$
 
@@
          {
-           \beta_j^{j \in J_2},\Pred\,^2,\Post^2 }
-         {s_0^2 \OTarrow {\alpha} s_1^2} 
+           \beta_j^{j \in J_2},\Pred_2,\Post_2 }
+         {s_{20} \OTarrow {\alpha} s_{21}} 
 \end{mathpar}
 For each of the weak open transition obtained above, we have the following.
-We have $(s_1^1,t_x|\Pred_{s_1^1,t_x})\in \mathcal{R}$, then $(s_0^2,t_x|\Pred_{s_0^2,t_x})\in \mathcal{R}$. Again 
+We have $(s_{11},t_x|\Pred_{s_{11},t_x})\in \mathcal{R}$, then $(s_{20},t_x|\Pred_{s_{20},t_x})\in \mathcal{R}$. Again 
  by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{x y}^{x\in X,y\in Y} \subseteq \WT_2$:
@@
 \end{mathpar}
- such that  $\forall x,\forall y, J_{xy}=\{j\in J_2|\beta^2_j\neq\tau\}, 
-(s_1^2,t_{x y}|\Pred_{s_1^2,t_{x y}})\in \mathcal{R}$; \\
- $\Pred_{s_1^1,t_x} \land \Pred\,^2\\
+ such that  $\forall x,\forall y, J_{xy}=\{j\in J_2|\beta_{2j}\neq\tau\}, 
+(s_{21},t_{x y}|\Pred_{s_{21},t_{x y}})\in \mathcal{R}$; \\
+ $\Pred_{s_{11},t_x} \land \Pred_2\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}}
- \!\!  \left( \forall j\in J_{x y}. \vis{\beta^2_j}\!=\!\gamma_{jx y}\Rightarrow \Pred_{OT_{x y}}\!\land \alpha\!=\!\alpha_{x y} \land  
-     \Pred_{s_1^2,t_{x y}}\subst{\Post^2\shortotimes\Post_{OT_{x y}}}\right)$
+ \!\!  \left( \forall j\in J_{x y}. \vis{\beta_{2j}}\!=\!\gamma_{jx y}\Rightarrow \Pred_{OT_{x y}}\!\land \alpha\!=\!\alpha_{x y} \land  
+     \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_{OT_{x y}}}\right)$
 
@@
     {
-       \set{\beta^3},\Pred^3,\Post^3   }
-         {s_0^3 \OTarrow {\tau} s_1^3} \in \mathcal{T}          
+       \set{\beta_3},\Pred_3,\Post_3   }
+         {s_{30} \OTarrow {\tau} s_{31}} \in \mathcal{T}          
 \end{mathpar}
 Additionally, we have 
-$(s_1^2,t_{x y}|\Pred_{s_0^3,t_{x y}})\in \mathcal{R}$, then $(s_0^3,t_{x y}|\Pred_{s_0^3,t_{x y}})\in \mathcal{R}$
+$(s_{21},t_{x y}|\Pred_{s_{30},t_{x y}})\in \mathcal{R}$, then $(s_{30},t_{x y}|\Pred_{s_{30},t_{x y}})\in \mathcal{R}$
 and by Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{x y z}^{x\in X,y\in Y,z\in Z} \subseteq \WT_2$:
@@
 \end{mathpar}
- such that  $\forall x, \forall y, \forall z,J_{xyz}= \{j\in J_3|\beta^3_j\neq\tau\}, 
-(s^3_1,t_{x y z}|\Pred_{s_1^3,t_{x y z}})\in \mathcal{R}$. \\
- $\Pred_{s_1^2,t_{x y}} \land \Pred^3\\
+ such that  $\forall x, \forall y, \forall z,J_{xyz}= \{j\in J_3|\beta_{3j}\neq\tau\}, 
+(s_{31},t_{x y z}|\Pred_{s_{31},t_{x y z}})\in \mathcal{R}$. \\
+ $\Pred_{s_{21},t_{x y}} \land \Pred_3\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{z\in Z}}
-   \!\left( \forall j\in J_{xyz}. \vis{\beta^3_j}\!=\!\gamma_{j x y z} \! \Rightarrow\! \Pred_{OT_{x y z}}\!
+   \!\left( \forall j\in J_{xyz}. \vis{\beta_{3j}}\!=\!\gamma_{j x y z} \! \Rightarrow\! \Pred_{OT_{x y z}}\!
      \land\! \alpha_{x y z}\!=\!\tau \land  
-     \Pred_{s^3_1,t_{x y z}}\subst{\Post^3\shortotimes\Post_{OT_{x y z}}}\right)$
+     \Pred_{s_{31},t_{x y z}}\subst{\Post_3\shortotimes\Post_{OT_{x y z}}}\right)$
 
@@
      \Pred_{s',t_{x y z}}\subst{\Post_{OT}\shortotimes\Post\,}\right)$
-We recall that we have:\\
-$\Pred_{OT}= \Pred^1 \wedge \Pred^2\subst{\Post^1} \wedge \Pred^3\subst{\Post^2\shortotimes\Post^1}$\\
-$\Post_{OT}=\Post^3\subst{\Post^2\shortotimes\Post^1}$\\
+Recall that we have:\\
+$\Pred_{OT}= \Pred_1 \wedge \Pred_2\subst{\Post_1} \wedge \Pred_3\subst{\Post_2\shortotimes\Post_1}$\\
+$\Post_{OT}=\Post_3\subst{\Post_2\shortotimes\Post_1}$\\
 Let's start with the statement:\\
-$\Pred_{s,t} \land \Pred^1\\
+$\Pred_{s,t} \land \Pred_1\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
- \! \! \left( \forall j\in J_x. \vis{\beta^1_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
+ \! \! \left( \forall j\in J_x. \vis{\beta_{1j}}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
      \land \alpha_x\!=\!\tau \land  
-     \Pred_{s_1^1,t_x}\subst{\Post^1\shortotimes\Post_{OT_x}}\right)$\\
+     \Pred_{s_{11},t_x}\subst{\Post_1\shortotimes\Post_{OT_x}}\right)$\\
 The conjunction of the term $\Pred^2\subst{\Post^1}$ with the both sides of the implication, we get:\\  
-$(\Pred_{s,t} \land \Pred^1)\wedge\Pred^2\subst{\Post^1}\\
+$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
  \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
-  \!\! \left( \forall j\in J_x. \vis{\beta^1_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
+  \!\! \left( \forall j\in J_x. \vis{\beta_{1j}}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
      \land \alpha_x\!=\!\tau \land  
-     \Pred_{s_1^1,t_x}\subst{\Post^1\shortotimes\Post_{OT_x}}\right) \wedge\Pred^2\subst{\Post^1\shortotimes\Post_{OT_x}}  \\
+     \Pred_{s_1^1,t_x}\subst{\Post^1\shortotimes\Post_{OT_x}}\right) \wedge\Pred_2\subst{\Post_1\shortotimes\Post_{OT_x}}  \\
 $
@@
 Hence a little rewriting gives:\\
-$(\Pred_{s,t} \land \Pred^1)\wedge\Pred^2\subst{\Post^1}\\
+$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
  \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
-\!\!   \left(\forall j\in J_x. \vis{\beta^1_j}\!=\!\gamma_{jx}\Rightarrow \Pred_{OT_x}
-     \!\land\! \alpha_x\!=\!\tau\land(\Pred_{s_1^1,t_x}\wedge\Pred^2)\subst{\Post^1\shortotimes\Post_{OT_x}} \right)$\\
-By replacing the inner sub-term $(\Pred_{s_1^1,t_x}\wedge\Pred^2)$ by the consequent of the corresponding implication given in case 2,  the formula becomes: \\
-$(\Pred_{s,t} \land \Pred^1)\wedge\Pred^2\subst{\Post^1}\\
+\!\!   \left(\forall j\in J_x. \vis{\beta_{1j}}\!=\!\gamma_{jx}\Rightarrow \Pred_{OT_x}
+     \!\land\! \alpha_x\!=\!\tau\land(\Pred_{s_{11},t_x}\wedge\Pred_2)\subst{\Post_1\shortotimes\Post_{OT_x}} \right)$\\
+By replacing the inner sub-term $(\Pred_{s_{11},t_x}\wedge\Pred_2)$ by the consequent of the corresponding implication given in case 2,  the formula becomes: \\
+$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
  \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
-   \!\!\Big(\forall j\in J_x. \vis{\beta^1_j}\!\!=\!\!\gamma_{jx}  \Rightarrow \Pred_{OT_x}
+   \!\!\Big(\forall j\in J_x. \vis{\beta_{1j}}\!\!=\!\!\gamma_{jx}  \Rightarrow \Pred_{OT_x}
      \!\land\! \alpha_x\!=\!\tau \land\Big(\displaystyle{\bigvee_{y\in Y}}
    ( \forall j\in J_{x y}.
-\vis{\beta^2_j}\!\!=\!\!\gamma_{jx y}\Rightarrow\\~~\qquad\quad \Pred_{OT_{x y}}\land \alpha\!=\!\alpha_{x y}\!
-\land \Pred_{s_1^2,t_{x y}}\subst{\Post^2\shortotimes\Post_{OT_{x y}}})\Big)\subst{\Post^1\shortotimes\Post_{OT_x}} \Big)$\\
+\vis{\beta_{2j}}\!\!=\!\!\gamma_{jx y}\Rightarrow\\~~\qquad\quad \Pred_{OT_{x y}}\land \alpha\!=\!\alpha_{x y}\!
+\land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_{OT_{x y}}})\Big)\subst{\Post_1\shortotimes\Post_{OT_x}} \Big)$\\
 Furthermore, the rewriting of the implication  gives:\\
-$(\Pred_{s,t} \land \Pred^1)\wedge\Pred^2\subst{\Post^1}\\
+$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} 
 \Big(\forall j\in J_x.
-\vis{\beta^1_j}\!\!=\!\!\gamma_{jx} \land  \forall j \in J_{x y}.
-\vis{\beta^2_j}\!\!=\!\gamma_{jx y}\Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \\\subst{\Post^1\shortotimes\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \land \Pred_{s_1^2,t_{x y}}\subst{\Post^2\shortotimes\Post^1\shortotimes \Post_{OT_{x y}}\shortotimes \Post_{OT_x}}\Big)$\\
-Finally, the conjunction with the term $\Pred^3\subst{\Post^2\shortotimes\Post^1}$ of the both sides of the implication and rewriting, we get:\\
-$(\Pred_{s,t} \land \Pred^1)\wedge\Pred^2\subst{\Post^1} \land \Pred^3\subst{\Post^2\shortotimes\Post^1}\\
+\vis{\beta_{1j}}\!\!=\!\!\gamma_{jx} \land  \forall j \in J_{x y}.
+\vis{\beta_{2j}}\!\!=\!\gamma_{jx y}\Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \\\subst{\Post_1\shortotimes\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_1\shortotimes \Post_{OT_{x y}}\shortotimes \Post_{OT_x}}\Big)$\\
+Finally, the conjunction with the term $\Pred_3\subst{\Post_2\shortotimes\Post_1}$ of the both sides of the implication and rewriting, we get:\\
+$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} 
 \Big(\forall j\in J_x.\vis{\beta^1_j}\!=\!\gamma_{jx} \land  \forall j \in J_{x y}.
-\vis{\beta^2_j}\!=\!\gamma_{jx y} \Rightarrow \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \alpha_x\!=\!
-\tau \land \alpha\!=\! \alpha_{x y} \land (\Pred_{s_1^2,t_{xy}} \land  \Pred^3) \subst{\Post^2\shortotimes \Post^1\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$\\ 
-Again because of the domain independence of the substitution, we deleted $\subst{\Post^1}$, and  we have added  $\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}$ on the right side of the implication.
-Finally, by replacing $(\Pred_{s_1^2,t_{xy}} \land  \Pred^3)$
+\vis{\beta_{2j}}\!=\!\gamma_{jx y} \Rightarrow \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \alpha_x\!=\!
+\tau \land \alpha\!=\! \alpha_{x y} \land (\Pred_{s_{21},t_{xy}} \land  \Pred_3) \subst{\Post_2\shortotimes \Post_1\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$\\ 
+Again because of the domain independence of the substitution, we deleted $\subst{\Post_1}$, and  we have added  $\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}$ on the right side of the implication.
+Finally, by replacing $(\Pred_{s_{21},t_{xy}} \land  \Pred_3)$
 by the consequent of the corresponding implication given in case 3, we get:\\
-$(\Pred_{s,t} \land \Pred^1)\land \Pred^2\subst{\Post^1} \land \Pred^3\subst{\Post^2\shortotimes\Post^1}\\
+$(\Pred_{s,t} \land \Pred_1)\land \Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} \displaystyle{\bigvee_{z\in Z}} 
-\Big(\forall j\in J_x.\vis{\beta^1_j}\!\!=\!\!\gamma_{jx} \land\!
+\Big(\forall j\in J_x.\vis{\beta_{1j}}\!\!=\!\!\gamma_{jx} \land\!
 \forall j \!\in\!
-J_{x y}.\vis{\beta^2_j}\!\!=\!\!\gamma_{jx y} \forall j\!\in\!
+J_{x y}.\vis{\beta_{2j}}\!\!=\!\!\gamma_{jx y} \forall j\!\in\!
 J_{x y z}.
-\vis{\beta^3_j}\!\!=\!\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\!\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \land \alpha_x\!=\!
-\tau \!\land \alpha\!=\!\alpha_{x y} \land \alpha_{x y z}\!=\!\tau \land \Pred_{s^3_1,t_{x y z}}  \subst{\underbrace{\Post^3\shortotimes\Post^2\shortotimes\Post^1}_{\Post_{OT}}\,\shortotimes \Post_{OT_{x y z}}\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$
-Therefore, having $s^3_1=s'$ we can conclude:\\
-$(\Pred_{s,t} \land \Pred^1)\land \Pred^2\subst{\Post^1} \land \Pred^3\subst{\Post^2\shortotimes\Post^1}\\
+\vis{\beta_{3j}}\!\!=\!\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\!\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \land \alpha_x\!=\!
+\tau \!\land \alpha\!=\!\alpha_{x y} \land \alpha_{x y z}\!=\!\tau \land \Pred_{s_{31},t_{x y z}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post^1}_{\Post_{OT}}\,\shortotimes \Post_{OT_{x y z}}\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$
+Therefore, having $s_{31}=s'$ we can conclude:\\
+$(\Pred_{s,t} \land \Pred_1)\land \Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} \displaystyle{\bigvee_{z\in Z}} 
 \Big(\forall j\in J_{x y z}.
-\vis{\beta^1_j}.\vis{\beta^2_j}.\vis{\beta^3_j}\!=\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \land \alpha\!=\!\alpha_{x y} \land \Pred_{s',t_{x y z}}\subst{\Post_{OT}\shortotimes\Post_{OT_{x y z}}\shortotimes\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$
+\vis{\beta^1_j}.\vis{\beta_{2j}}.\vis{\beta_{3j}}\!=\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \land \alpha\!=\!\alpha_{x y} \land \Pred_{s',t_{x y z}}\subst{\Post_{OT}\shortotimes\Post_{OT_{x y z}}\shortotimes\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$
 This is exactly what we needed to prove. \qed

### 2019-05-03 2016-Weak-FH-Bisim/WeakBisim.tex
progressed but not yet finished

@@
 $
-{\displaystyle \alpha''=\alpha\subst{\bigotimes_{j=n_1+n_2}^{0}\Post_{4j}}}\\
+{\displaystyle \alpha''=\alpha\subst{\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}\!}\\
 s\!=\!s_{40} \wedge s_{4(n_1+n_2+1)}\!=s_2 \wedge s_2' = s_{50} \wedge s_{5(m_1+m_2+1)}\!=\!s'\\
 ~~\\
-\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2} \vis{\set{\beta_{4i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{4 j} } }  \dotcup  \vis{\set{\beta'}\subst{\bigotimes_{j=n_1+n_2}^{0}\Post_{4j}}}}\\~\qquad
-\dotcup\!\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta_{5i}}\subst{\bigotimes_{j=i-1}^{0}\Post'_{5i}\shortotimes\Post\,'\shortotimes\bigotimes_{j=n_1+n_2}^{0}\Post_{4i}} }
+\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2} \vis{\set{\beta_{4i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{4 j} } }  \dotcup  \vis{\set{\beta'}\subst{\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}}}\\~\qquad
+\dotcup\!\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta_{5i}}\subst{\bigotimes_{j=i-1}^{0}\Post'_{5i}\shortotimes\Post\,'\shortotimes\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4i}} }
 \\
 \displaystyle{\Pred=
-\bigwedge_{i=0}^{n_1+n_2}\!\!\Pred_{4i}\subst{\bigotimes_{j=i-1}^{0}\Post_{4j}}\land\Pred\,' \subst{\bigotimes_{j={n_1+n_2}}^{0}\Post_{4j}}\land}\\ 
-~\qquad\quad\Big(\bigwedge_{i=0}^{m_1+m_2}\Pred_{5i}\subst{\bigotimes_{j=i-1}^{0}\Post_{5j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_1+n_2}}^{0}\Post_{4j}}\Big)\\
-\Post=\bigotimes_{j=m_1+m_2}^{0}\!\!\Post_{5j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_1+n_2}}^{0}\Post_{4j}
+\bigwedge_{i=0}^{n_1+n_2}\!\!\Pred_{4i}\subst{\bigotimes_{j=i-1}^{0}\Post_{4j}}\land\Pred\,' \subst{\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\!\Post_{4j}}\land}\\ 
+~\qquad\quad\bigwedge_{i=0}^{m_1+m_2}\Pred_{5i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{5j}\shortotimes\Post\,'\shortotimes\!\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\!\Post_{4j}}\\
+\Post=\bigotimes_{j=m_1+m_2}^{0}\!\!\!\Post_{5j}\shortotimes\Post\,'\shortotimes\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\Post_{4j}
 $\\
@@
 $s\in\mathcal{S}_1$ and
-$t\in\mathcal{S}_2$ such that $(s,t|\Pred)\in\mathcal{R}$, we 
+$t\in\mathcal{S}_2$ such that $(s,t|\Pred_{s,t})\in\mathcal{R}$, we 
    have:
@@
          {
-           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
+           \gamma_j^{j\in J'},\Pred_{OT},\Post_{OT}}
          {s \OTWeakarrow {\alpha} s'}
@@
 \end{mathpar}
- such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
+ such that  $\forall x, J'=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
  and  \\
-$\Pred \land \Pred_{OT}\\
+$\Pred_{s,t} \land \Pred_{OT}\\
 \displaystyle{\implies\!\!\! \bigvee_{x\in X}
@@
 ($\Rightarrow$) Firstly, we prove that Definition \ref{def-Weak-bisim} implies definition above.\\
-Suppose that $\Pred_{s,t}\in \mathcal{R}$ and for any open transition $OT$ in $\mathcal{T}_1$:
- \begin{mathpar}
-     \openrule
-         {
-           \beta_j^{j\in J},\Pred_{OT},\Post_{OT}}
-         {s \OTarrow {\alpha} s'}
-
-\end{mathpar}
-there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {t \OTWeakarrow {\alpha_x} t_x}
-\end{mathpar}
- such that  $\forall x, J_{x}=\{j\in J|\beta_j\neq\tau\}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
- and  \\
- $\Pred_{s,t} \land \Pred_{OT}\\
- \implies\!\!\!\displaystyle{\bigvee_{x\in X}}
-   \big(\forall j\in J_x. \vis{\beta_j}=\gamma_{jx}\Rightarrow \Pred_{OT_x}
-     \land \alpha\!=\!\alpha_x\land  
-     \Pred_{s',t_x}\subst{\Post_{OT}\shortotimes\Post_{OT_x}}\big)$\\
-and  suppose the following statement holds:
-\begin{mathpar}
-     \openrule
-         {
-           \gamma_j^{j\in J},\Pred_{OT},\Post_{OT}}
-         {s \OTWeakarrow {\alpha} s'}
+Suppose that $\Pred_{s,t}\in \mathcal{R}$ 
+%and for any open transition $OT$ in $\mathcal{T}_1$:
+% \begin{mathpar}
+%     \openrule
+%         {
+%           \beta_j^{j\in J},\Pred_{OT},\Post_{OT}}
+%         {s \OTarrow {\alpha} s'}
+%\end{mathpar}
+%there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
+% \begin{mathpar}
+%    \openrule
+%         {
+%           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+%         {t \OTWeakarrow {\alpha_x} t_x}
+%\end{mathpar}
+% such that  $\forall x, J_{x}=\{j\in J|\beta_j\neq\tau\}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
+% and  \\
+% $\Pred_{s,t} \land \Pred_{OT}\\
+% \implies\!\!\!\displaystyle{\bigvee_{x\in X}}
+%   \big(\forall j\in J_x. \vis{\beta_j}=\gamma_{jx}\Rightarrow \Pred_{OT_x}
+%     \land \alpha\!=\!\alpha_x\land  
+%     \Pred_{s',t_x}\subst{\Post_{OT}\shortotimes\Post_{OT_x}}\big)$\\
+and  suppose that the following statement holds:
+\begin{mathpar}
+     \openrule
+         {
+           \gamma_j^{j\in J'},\Pred_{OT},\Post_{OT}}
+         {s \OTWeakarrow {\alpha} s'} \in \WT_1
 
@@
          {
-           \gamma_j^{j\in J},\Pred_{OT},\Post_{OT}}
-         {s \OTWeakarrow {\alpha} s'}
+           \gamma_j^{j\in J'},\Pred_{OT},\Post_{OT}}
+         {s \OTWeakarrow {\alpha} s'} \in \WT_1
          \implies
@@
     {
-       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
-         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T}  \wedge
-
-\openrule
-         {
-           \set{\beta_2},\Pred_2,\Post_2 }
-         {s_{20} \OTarrow {\alpha} s_{21}} \in \mathcal{T}
+       \beta_{1ij}^{j\in J_1'},\Pred_{1i},\Post_{1i}   }
+         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T}_1  \wedge
+
+\openrule
+         {
+           \beta_{2j}^{j\in J_2'},\Pred_2,\Post_2 }
+         {s_{20} \OTarrow {\alpha} s_{21}} \in \mathcal{T}_1
  \wedge
@@
          {
-           \set{\beta_{3i}},\Pred_{3i},  \Post_{3i}  }
-         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}
+           \beta_{3ij}^{j\in J_3'},\Pred_{3i},  \Post_{3i}  }
+         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}_1
 \bigg)
@@
 \displaystyle{
-\gamma_j^{j\in J}=\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
+\gamma_j^{j\in J'}=\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
 \\
@@
 \begin{enumerate}
-\item For the first open transition:
+\item For the first open transition in $\mathcal{T}_1$:
 \begin{mathpar}
@@
     {
-       \set{\beta_{10}},\Pred_{10},\Post_{10}   }
-         {s_{10} \OTarrow {\tau} s_{11}} \in \mathcal{T}          
+       \beta_{1j}^{j\in J_1'},\Pred_1,\Post_1   }
+         {s_{10} \OTarrow {\tau} s_{11}}          
 \end{mathpar}
-we have $(s,t|\Pred_{s,t})\in\mathcal{R}$, hence $(s_{10},t|\Pred_{s_{10},t})\in\mathcal{R}$, since $s=s_{10}$.
-By  Definition \ref{def-Weak-bisim} we  can deduce there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
+we have $(s,t|\Pred_{s,t})\in\mathcal{R}$ by hypothesis, and $s=s_{10}$ the we have $(s_{10},t|\Pred_{s_{10},t})\in\mathcal{R}$.
+Thus, by  Definition \ref{def-Weak-bisim} we  can deduce there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
  \begin{mathpar}
@@
 \end{mathpar}
- such that  $\forall x,J_{x}=\{j\in J|\beta_{1j}\neq\tau\}, (s_{11},t_x|\Pred_{s_{11},t_x})\in \mathcal{R}$. \\
- $\Pred_{s,t} \land \Pred^1\\
+ such that  $\forall x,J_{x}=\{j\in J_1'|\beta_{1j}\neq\tau\}, (s_{11},t_x|\Pred_{s_{11},t_x})\in \mathcal{R}$. \\
+ $\Pred_{s,t} \land \Pred_1\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
@@
 \end{mathpar}
-\item Concerning the middle open transition, we have:
- \begin{mathpar}
-     \openrule
-         {
-           \beta_j^{j \in J_2},\Pred_2,\Post_2 }
+\item Concerning the middle open transition in $\mathcal{T}_1$, we have:
+ \begin{mathpar}
+     \openrule
+         {
+           \beta_{2j}^{j \in J_2'},\Pred_2,\Post_2 }
          {s_{20} \OTarrow {\alpha} s_{21}} 
 \end{mathpar}
-For each of the weak open transition obtained above, we have the following.
-We have $(s_{11},t_x|\Pred_{s_{11},t_x})\in \mathcal{R}$, then $(s_{20},t_x|\Pred_{s_{20},t_x})\in \mathcal{R}$. Again 
+For each of the weak open transition obtained above, we have  $(s_{11},t_x|\Pred_{s_{11},t_x})\in \mathcal{R}$  and $s_{11}=s_{20}$, so we have  $(s_{20},t_x|\Pred_{s_{20},t_x})\in \mathcal{R}$.
+Again
  by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{x y}^{x\in X,y\in Y} \subseteq \WT_2$:
@@
 \end{mathpar}
- such that  $\forall x,\forall y, J_{xy}=\{j\in J_2|\beta_{2j}\neq\tau\}, 
+ such that  $\forall x,\forall y, J_{xy}=\{j\in J_2'|\beta_{2j}\neq\tau\}, 
 (s_{21},t_{x y}|\Pred_{s_{21},t_{x y}})\in \mathcal{R}$; \\
@@
 
-\item 
-And similarly, for the third  open transition:
+\item Similarly to the case 1,  the third  open transition in $\mathcal{T}_1$:
      \begin{mathpar}
@@
     {
-       \set{\beta_3},\Pred_3,\Post_3   }
+       \beta_{3j}^{j \in J_3'},\Pred_3,\Post_3   }
          {s_{30} \OTarrow {\tau} s_{31}} \in \mathcal{T}          
 \end{mathpar}
-Additionally, we have 
-$(s_{21},t_{x y}|\Pred_{s_{30},t_{x y}})\in \mathcal{R}$, then $(s_{30},t_{x y}|\Pred_{s_{30},t_{x y}})\in \mathcal{R}$
-and by Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{x y z}^{x\in X,y\in Y,z\in Z} \subseteq \WT_2$:
+From previous case, we have $(s_{21},t_{x y}|\Pred_{s_{21},t_{x y}})\in \mathcal{R}$, and we have $s_{21}=s_{30}$ then we have $(s_{30},t_{x y}|\Pred_{s_{30},t_{x y}})\in \mathcal{R}$. By
+ Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{x y z}^{x\in X,y\in Y,z\in Z} \subseteq \WT_2$:
  \begin{mathpar}
@@
 \end{mathpar}
- such that  $\forall x, \forall y, \forall z,J_{xyz}= \{j\in J_3|\beta_{3j}\neq\tau\}, 
+ such that  $\forall x, \forall y, \forall z,J_{xyz}= \{j\in J_3'|\beta_{3j}\neq\tau\}, 
 (s_{31},t_{x y z}|\Pred_{s_{31},t_{x y z}})\in \mathcal{R}$. \\
@@
 \medskip     
-
-Moreover, by applying (\WTTrois)~rule on the resulting $\symb{WOT}$s we have:
+Based on cases described above by applying (\WTTrois)~rule on the resulting $\symb{WOT}$s we have:
 
@@
 \\
-\Pred=\Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}}\land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}
-}
-{
-\openrule
-         {
-           \gamma_{j x}^{j\in J_{x}} \dotcup \gamma_{j x y}^{j\in J_{x y}}\dotcup\gamma_{j x y z}^{j\in J_{x y z}},
-		\Pred, \Post_{OT_{x y z}}\subst {\Post_{OT_{x y}}\shortotimes\Post_{OT_{x}}}}  
-         {t \OTWeakarrow {\alpha_{x y}} t_{x y z}} 
+\set{\gamma}=\gamma_{j x}^{j\in J_{x}} \dotcup \gamma_{j x y}^{j\in J_{x y}} \subst{\Post_{OT_x}} \dotcup\gamma_{j x y z}^{j\in J_{x y z}} \subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}\\
+\Pred=\Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}}\land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}\\
+\Post= \Post_{OT_{x y z}} \shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_{x}}\quad \alpha'_{x y}=\alpha_{x y}\subst{\Post_{OT_x}}\\
+}
+{
+\openrule
+         {
+           \set{\gamma},
+		\Pred, \Post}  
+         {t \OTWeakarrow {\alpha'_{x y}} t_{x y z}} 
 } 
@@
    \left( \forall j\in J_{x y z}. \gamma_j=\gamma_{j x y z}  \Rightarrow \Pred_{OT_{x y z}}
-     \land \alpha \!=\! \alpha_{x y} \land  
+     \land \alpha \!=\! \alpha_{x y}' \land  
      \Pred_{s',t_{x y z}}\subst{\Post_{OT}\shortotimes\Post\,}\right)$
-Recall that we have:\\
+Let's start with the hypothesis we have:\\
 $\Pred_{OT}= \Pred_1 \wedge \Pred_2\subst{\Post_1} \wedge \Pred_3\subst{\Post_2\shortotimes\Post_1}$\\
-$\Post_{OT}=\Post_3\subst{\Post_2\shortotimes\Post_1}$\\
-Let's start with the statement:\\
+$\Post_{OT}=\Post_3\shortotimes \Post_2\shortotimes\Post_1$\\
+Moreover, we have the following the statement:\\
 $\Pred_{s,t} \land \Pred_1\\
@@
      \Pred_{s_{11},t_x}\subst{\Post_1\shortotimes\Post_{OT_x}}\right)$\\
-The conjunction of the term $\Pred^2\subst{\Post^1}$ with the both sides of the implication, we get:\\  
+The conjunction of the term $\Pred_2\subst{\Post_1}$ with the both sides of the implication, we get:\\  
 $(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
@@
      \land \alpha_x\!=\!\tau \land  
-     \Pred_{s_1^1,t_x}\subst{\Post^1\shortotimes\Post_{OT_x}}\right) \wedge\Pred_2\subst{\Post_1\shortotimes\Post_{OT_x}}  \\
+     \Pred_{s_{11},t_x}\subst{\Post_1\shortotimes\Post_{OT_x}}\right) \wedge\Pred_2\subst{\Post_1\shortotimes\Post_{OT_x}}  \\
 $
-Note because of the domain independence of the substitution, we have also added the substitution $\subst{\Post_{OT_x}}$ on the right side of the implication without affecting the validity of the statement.
+Note that we added  the substitution $\subst{\Post_{OT_x}}$ on the right side of the implication without affecting the validity of the statement, because of the domain independence of the substitution.
 Hence a little rewriting gives:\\
@@
      \!\land\! \alpha_x\!=\!\tau\land(\Pred_{s_{11},t_x}\wedge\Pred_2)\subst{\Post_1\shortotimes\Post_{OT_x}} \right)$\\
-By replacing the inner sub-term $(\Pred_{s_{11},t_x}\wedge\Pred_2)$ by the consequent of the corresponding implication given in case 2,  the formula becomes: \\
+By replacing the inner sub-term $(\Pred_{s_{11},t_x}\wedge\Pred_2)$ by the conclusion of the corresponding implication given in case 2,  the formula becomes: \\
 $(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
  \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
-   \!\!\Big(\forall j\in J_x. \vis{\beta_{1j}}\!\!=\!\!\gamma_{jx}  \Rightarrow \Pred_{OT_x}
+   \!\!\Big(\forall j\in J_x. \vis{\beta_{1j}}\!\!=\!\gamma_{jx}  \Rightarrow \Pred_{OT_x}
      \!\land\! \alpha_x\!=\!\tau \land\Big(\displaystyle{\bigvee_{y\in Y}}
@@
 \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_{OT_{x y}}})\Big)\subst{\Post_1\shortotimes\Post_{OT_x}} \Big)$\\
-Furthermore, the rewriting of the implication  gives:\\
+Furthermore, the rewriting of the formula  gives:\\
 $(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
@@
 \tau \land \alpha\!=\! \alpha_{x y} \land (\Pred_{s_{21},t_{xy}} \land  \Pred_3) \subst{\Post_2\shortotimes \Post_1\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$\\ 
-Again because of the domain independence of the substitution, we deleted $\subst{\Post_1}$, and  we have added  $\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}$ on the right side of the implication.
+Again note that because of the domain independence of the substitution, we deleted $\subst{\Post_1}$, and  we  added  $\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}$ on the right side of the implication.\\
+
 Finally, by replacing $(\Pred_{s_{21},t_{xy}} \land  \Pred_3)$
-by the consequent of the corresponding implication given in case 3, we get:\\
+by the conclusion of the corresponding implication given in case 3, we get:\\
 $(\Pred_{s,t} \land \Pred_1)\land \Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\\
@@
 \vis{\beta_{3j}}\!\!=\!\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\!\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \land \alpha_x\!=\!
-\tau \!\land \alpha\!=\!\alpha_{x y} \land \alpha_{x y z}\!=\!\tau \land \Pred_{s_{31},t_{x y z}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post^1}_{\Post_{OT}}\,\shortotimes \Post_{OT_{x y z}}\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$
+\tau \!\land \alpha\!=\!\alpha_{x y} \land \alpha_{x y z}\!=\!\tau \land \Pred_{s_{31},t_{x y z}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\shortotimes \,\Post_{OT_{x y z}}\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$
+
 Therefore, having $s_{31}=s'$ we can conclude:\\

### 2019-05-03 2016-Weak-FH-Bisim/WeakBisim.tex
suite lemma

@@
 $\Pred_{s,t} \land \Pred\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{z\in Z}}
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}}\displaystyle{\bigvee_{z\in Z}}
    \left( \forall j\in J_{x y z}. \gamma_j=\gamma_{j x y z}  \Rightarrow \Pred_{OT_{x y z}}
@@
 $
-Note that we added  the substitution $\subst{\Post_{OT_x}}$ on the right side of the implication without affecting the validity of the statement, because of the domain independence of the substitution.
+Note that  on the right side of the implication we added  the substitution  of $\Post_{OT_x}$ without affecting the validity of the statement, because of the domain independence of the substitution \TODO{l'argument ne me convainc pas}.
 Hence a little rewriting gives:\\
@@
      \!\land\! \alpha_x\!=\!\tau\land(\Pred_{s_{11},t_x}\wedge\Pred_2)\subst{\Post_1\shortotimes\Post_{OT_x}} \right)$\\
-By replacing the inner sub-term $(\Pred_{s_{11},t_x}\wedge\Pred_2)$ by the conclusion of the corresponding implication given in case 2,  the formula becomes: \\
+By replacing the inner sub-term $(\Pred_{s_{11},t_x}\wedge\Pred_2)$ by the conclusion of the  implication given in case 2,  the formula becomes: \\
 $(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
@@
    ( \forall j\in J_{x y}.
-\vis{\beta_{2j}}\!\!=\!\!\gamma_{jx y}\Rightarrow\\~~\qquad\quad \Pred_{OT_{x y}}\land \alpha\!=\!\alpha_{x y}\!
+\vis{\beta_{2j}}\!\!=\!\!\gamma_{jx y} \\ \Rightarrow \Pred_{OT_{x y}}\land \alpha\!=\!\alpha_{x y}\!
 \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_{OT_{x y}}})\Big)\subst{\Post_1\shortotimes\Post_{OT_x}} \Big)$\\
@@
 \vis{\beta_{1j}}\!\!=\!\!\gamma_{jx} \land  \forall j \in J_{x y}.
-\vis{\beta_{2j}}\!\!=\!\gamma_{jx y}\Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \\\subst{\Post_1\shortotimes\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_1\shortotimes \Post_{OT_{x y}}\shortotimes \Post_{OT_x}}\Big)$\\
+\vis{\beta_{2j}}\subst{\Post_1\shortotimes\Post_{OT_x}} \!=\!\gamma_{jx y}  \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_1\shortotimes\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \subst{\Post_1\shortotimes\Post_{OT_x}} \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_1\shortotimes \Post_{OT_{x y}}\shortotimes \Post_{OT_x}}\Big)$\\
+As $Post_1$  does not act on $\gamma_{jx y}$, nor on $ \Pred_{OT_{x y}}$ and $  \alpha_{x y}$, the formula can be simplified as follows:\\
+$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} 
+\Big(\forall j\in J_x.
+\vis{\beta_{1j}}\!=\!\gamma_{jx} \land  \forall j \in J_{x y}.
+\vis{\beta_{2j}}\subst{\Post_{OT_x}}\!=\!\gamma_{jx y}   \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \subst{\Post_{OT_x}} \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_1\shortotimes \Post_{OT_{x y}}\shortotimes \Post_{OT_x}}\Big)$\\
 Finally, the conjunction with the term $\Pred_3\subst{\Post_2\shortotimes\Post_1}$ of the both sides of the implication and rewriting, we get:\\
@@
 \Big(\forall j\in J_x.\vis{\beta^1_j}\!=\!\gamma_{jx} \land  \forall j \in J_{x y}.
-\vis{\beta_{2j}}\!=\!\gamma_{jx y} \Rightarrow \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \alpha_x\!=\!
-\tau \land \alpha\!=\! \alpha_{x y} \land (\Pred_{s_{21},t_{xy}} \land  \Pred_3) \subst{\Post_2\shortotimes \Post_1\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$\\ 
-Again note that because of the domain independence of the substitution, we deleted $\subst{\Post_1}$, and  we  added  $\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}$ on the right side of the implication.\\
-
+\vis{\beta_{2j}}\subst{\Post_{OT_x}} \!=\!\gamma_{jx y} \Rightarrow \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \alpha_x\!=\!
+\tau \land \alpha\!=\! \alpha_{x y} \subst{\Post_{OT_x}} \land (\Pred_{s_{21},t_{xy}} \land  \Pred_3) \subst{\Post_2\shortotimes \Post_1\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$\\ 
+Again note that because of the domain independence of the substitution, we removed $\Post_1$ and  we  added  $\Post_{OT_{x y}}\shortotimes\,\Post_{OT_x}$ on the right side of the implication.\\
 Finally, by replacing $(\Pred_{s_{21},t_{xy}} \land  \Pred_3)$
-by the conclusion of the corresponding implication given in case 3, we get:\\
+by the conclusion of the  implication given in case 3, we get:\\
 $(\Pred_{s,t} \land \Pred_1)\land \Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} \displaystyle{\bigvee_{z\in Z}} 
-\Big(\forall j\in J_x.\vis{\beta_{1j}}\!\!=\!\!\gamma_{jx} \land\!
-\forall j \!\in\!
-J_{x y}.\vis{\beta_{2j}}\!\!=\!\!\gamma_{jx y} \forall j\!\in\!
-J_{x y z}.
-\vis{\beta_{3j}}\!\!=\!\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\!\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \land \alpha_x\!=\!
-\tau \!\land \alpha\!=\!\alpha_{x y} \land \alpha_{x y z}\!=\!\tau \land \Pred_{s_{31},t_{x y z}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\shortotimes \,\Post_{OT_{x y z}}\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$
-
-Therefore, having $s_{31}=s'$ we can conclude:\\
+\hspace{1cm} \implies\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} \displaystyle{\bigvee_{z\in Z}} 
+\Big(\forall j\in J_x.\vis{\beta_{1j}}\!=\!\gamma_{jx} \land\!  \forall j \!\in\! J_{x y}.\vis{\beta_{2j}}\subst{\Post_{OT_x}}\!=\!\gamma_{jx y}   \land \\
+ \forall j\!\in\! J_{x y z}. \vis{\beta_{3j}} \subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \!=\!\gamma_{j x y z}  \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}} \subst{\Post_{OT_x}} \land \\
+  \Pred_{OT_{x y z}}\!\subst{\Post_{OT_{x y}}\shortotimes\,\Post_{OT_x}} \land \alpha_x\!=\!
+\tau \!\land \alpha\!=\!\alpha_{x y} \subst{\Post_{OT_x}}\land \alpha_{x y z}\!=\!\tau \land \Pred_{s_{31},t_{x y z}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\shortotimes \,\Post_{OT_{x y z}}\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$\\
+Having $s_{31}=s'$ we can conclude:\\
 $(\Pred_{s,t} \land \Pred_1)\land \Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\\
@@
 \Big(\forall j\in J_{x y z}.
-\vis{\beta^1_j}.\vis{\beta_{2j}}.\vis{\beta_{3j}}\!=\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \land \alpha\!=\!\alpha_{x y} \land \Pred_{s',t_{x y z}}\subst{\Post_{OT}\shortotimes\Post_{OT_{x y z}}\shortotimes\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$
+\vis{\beta^1_j}.\vis{\beta_{2j}}\subst{\Post_{OT_x}}.\vis{\beta_{3j}}\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \!=\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \land \alpha\!=\!\alpha_{x y}\subst{\Post_{OT_x}} \land \Pred_{s',t_{x y z}}\subst{\Post_{OT}\shortotimes\Post_{OT_{x y z}}\shortotimes\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$\\
+ \TODO{gamma ne me convainc pas et je dois generaliser}
 This is exactly what we needed to prove. \qed

### 2019-05-07 2016-Weak-FH-Bisim/WeakBisim.tex
double formula
skype meeting

@@
      %     \right)$.
-\bigskip
-
- $\Pred_{s,t} \land \Pred_{OT}\implies\bigvee_{x\in X} \Pred_x$
-and\\
-%\hspace{1cm}
- $ \forall{x\in X}. \Pred_x \land \Pred_{s,t} \land \Pred_{OT} \Rightarrow
-   \left( \forall j. \beta_j=\beta_{jx}  \land \Pred_{OT_x}
-     \land \alpha\!=\!\alpha_x \land  
-     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)$
-     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
-     %     \right)$.
+%\bigskip
+%
+% $\Pred_{s,t} \land \Pred_{OT}\implies\bigvee_{x\in X} \Pred_x$
+%and\\
+%%\hspace{1cm}
+% $ \forall{x\in X}. \Pred_x \land \Pred_{s,t} \land \Pred_{OT} \Rightarrow
+%   \left( \forall j. \beta_j=\beta_{jx}  \land \Pred_{OT_x}
+%     \land \alpha\!=\!\alpha_x \land  
+%     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)$
+%     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
+%     %     \right)$.
 
@@
      \land \alpha\!=\!\alpha_x \land  
-     \Pred_{s',t_x}\subst{\Post_{OT}\shortotimes\Post_{OT_x}}\right)$
+     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)$
 
@@
        	\land \alpha\!=\!\alpha_{px} \land
-       	\Pred_{{px}}\subst{\Post_{OT}\shortotimes\Post_{OT_{px}}}\right)$\\
+       	\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\right)$\\
 
@@
        	\land \alpha_{px}\!=\!\alpha_{pxy} \land
-       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}\shortotimes\Post_{OT_{pxy}}}\right)$.\\
+       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}\right)$.\\
 
@@
        		\land \alpha\!=\!\alpha_{pxy} \land
-       		\Pred\,'_{{pxy}}\subst{\Post_{OT}\shortotimes\Post_{OT_{pxy}}}\right)$.
+       		\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{pxy}}}\right)$.
        	\end{small}
@@
        		\land \alpha\!=\!\alpha_{px} \land
-       		\Pred_{{px}}\subst{\Post_{OT}\shortotimes\Post_{OT_{px}}}\right)\land\Pred_{p,u}\\
+       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\right)\land\Pred_{p,u}\\
        		%
@@
        		\land \alpha\!=\!\alpha_{px} \land
-       		\Pred_{{px}}\subst{\Post_{OT}\shortotimes\Post_{OT_{px}}}\right)\\
+       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\right)\\
        		%
@@
        		\land \alpha_{px}\!=\!\alpha_{pxy}\\\hspace{3em}~ \land
-       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}\shortotimes\Post_{OT_{pxy}}}\big))
+       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}\big))
        		\land \alpha\!=\!\alpha_{px} \land
-       		\Pred_{{px}}\subst{\Post_{OT}\shortotimes\Post_{OT_{px}}}\big)\\
+       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\big)\\
        		%
@@
        		\land \alpha\!=\alpha_{px}\!=\!\alpha_{pxy}\\\hspace{3em}~ \land
-       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}\shortotimes\Post_{OT_{pxy}}}
+       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}
        		\land
-       		\Pred_{{px}}\subst{\Post_{OT}\shortotimes\Post_{OT_{px}}}\big)\big)
+       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\big)\big)
        		$
@@
 substitutions  and of the predicates, we have:\\
-       	$\Pred_{{px}}\subst{\Post_{OT}\shortotimes\Post_{OT_{px}}}\land 
-       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}\shortotimes\Post_{OT_{pxy}}}\\
+       	$\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\land 
+       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}\\
        	\Leftrightarrow % we changed =
-       	\Pred_{{px}}\subst{\Post_{OT}\shortotimes\Post_{OT_{px}}\shortotimes\Post_{OT_{pxy}}}\land
-       	\Pred_{{pxy}}\subst{\Post_{OT}\shortotimes\Post_{OT_{px}}\shortotimes\Post_{OT_{pxy}}}\\
-       	\implies\Pred\,'_{{pxy}}\subst{\Post_{OT}\shortotimes\Post_{OT_{px}}\shortotimes\Post_{OT_{pxy}}}\\
+       	\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}\land
+       	\Pred_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}\\
+       	\implies\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}\\
        	\Leftrightarrow % we changed = 
-       	 \Pred\,'_{{pxy}}\subst{\Post_{OT}\shortotimes\Post_{OT_{pxy}}} $\\
+       	 \Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{pxy}}} $\\
 
@@
 \land \alpha\!=\alpha_{px}\!=\!\alpha_{pxy}\\~\hspace{3em}~ \land
-\Pred\,'_{{pxy}}\subst{\Post_{OT}\shortotimes\Post_{OT_{pxy}}}\big)\big)
+\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{pxy}}}\big)\big)
 \\
@@
 \land \alpha\!=\!\alpha_{pxy} \land
-\Pred\,'_{{pxy}}\subst{\Post_{OT}\shortotimes\Post_{OT_{pxy}}}\right)$.
+\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{pxy}}}\right)$.
   \end{small}
@@
  \land \alpha_Q\!=\!\alpha_x \land  
- \Pred_{s x}\subst{\Post\,''\shortotimes\Post_{OT_x}}\right)$
+ \Pred_{s x}\subst{\Post\,''\uplus\Post_{OT_x}}\right)$
 
@@
  	\land \alpha_Q\!=\!\alpha_x \land  
- 	\Pred_{s x}\subst{\Post\,''\shortotimes\Post_{OT_x}}\right)
+ 	\Pred_{s x}\subst{\Post\,''\uplus\Post_{OT_x}}\right)
  }
@@
  		\land \alpha_Q\!=\!\alpha_x \land \alpha_Q\!=\!\beta_{j_0 x} \land  
- 		\Pred_{s x}\subst{\Post\,''\shortotimes\Post_{OT_x}}\right)
+ 		\Pred_{s x}\subst{\Post\,''\uplus\Post_{OT_x}}\right)
  	}
@@
  	\item Concerning the last term, we need 
- 	$\Pred_{s x}\subst{\Post_{OT}\shortotimes(\Post\,'\uplus \Post_{OT_x})}$ 
+ 	$\Pred_{s x}\subst{\Post_{OT}\uplus(\Post\,'\uplus \Post_{OT_x})}$ 
  	, i.e.:
  	$\Pred_{s x}\subst{(\Post\,'\uplus 
- 		\Post\,'')\shortotimes(\Post\,'\uplus \Post_{OT_x})}$. We 
+ 		\Post\,'')\uplus(\Post\,'\uplus \Post_{OT_x})}$. We 
  	can conclude by observing that	$\Pred_{s x}$ does not use any variable of $P$ 
@@
  		 \land \alpha_Q\!=\!\beta_{j_0 x}\right) \land \alpha_Q\!=\!\alpha_x\land  
- 		\Pred_{s x}\subst{\Post\,''\shortotimes\Post_{OT_x}}\right)
+ 		\Pred_{s x}\subst{\Post\,''\uplus\Post_{OT_x}}\right)
  	}\]
@@
 			\land \alpha\!=\!\alpha_x \land  
-			\Pred_{s x}\subst{\Post\,'\shortotimes\Post_{OT_x}}\right)$
+			\Pred_{s x}\subst{\Post\,'\uplus\Post_{OT_x}}\right)$
 			%     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x}) \right)$.
@@
 \land \alpha\!=\!\alpha_x}} %\\ \hspace*{40mm} %
-\land \Pred_{s x}\subst{\Post\,'\shortotimes\Post_{OT_x}}) \land
+\land \Pred_{s x}\subst{\Post\,'\uplus\Post_{OT_x}}) \land
 \Pred\,''\\ % 
@@
 \land \alpha\!=\!\alpha_x}} 
-\land \Pred_{s x}\subst{\Post\,'\shortotimes\Post_{OT_x}}) 	
+\land \Pred_{s x}\subst{\Post\,'\uplus\Post_{OT_x}}) 	
 $\end{small}
@@
 	change the validity of the formula (those variables are not used).
-	\item We need $\Pred_{s x}\subst{\Post_{OT}\shortotimes(\Post_{OT_x}\uplus \Post\,'')}$, i.e.:
-	$\Pred_{s x}\subst{(\Post\,'\uplus \Post\,'')\shortotimes(\Post_{OT_x}\uplus \Post\,'')}$. We 
+	\item We need $\Pred_{s x}\subst{\Post_{OT}\uplus(\Post_{OT_x}\uplus \Post\,'')}$, i.e.:
+	$\Pred_{s x}\subst{(\Post\,'\uplus \Post\,'')\uplus(\Post_{OT_x}\uplus \Post\,'')}$. We 
 	can conclude by observing that	$\Pred_{s x}$ does not use any variable of $Q$ 
@@
 We consider the case $n'=n+1$ (because $m'=m+1$ is similar).
-We first focus on the left part of the disjunction.
-Let us consider the sequence of ($n+m+1$) open transitions: \TODO{sur cette page coorection non faite}
+We want to prove (1) $\implies$ (2) in the lemma, and in (1) we  focus on the case where there is a set of open transitions (this is the case: $s\neq s'$).
+In other words, we consider the sequence of ($n+m+2$) open transitions:
 \begin{mathpar}
@@
 
-By recurrence hypothesis we suppose that the statement holds for $n$ and $m$ (we remove the first tau transition). We have:\\
+By recurrence hypothesis we suppose that the (1) $\implies$ (2) holds for $n$ and $m$ (compared to the line above, we remove the first $\tau$ transition). We have:\\
 
@@
 \, \wedge\\
-~~\hspace{5.25cm}\forall i \in [0..m].\openrule
+~~\hspace{2.25cm}\forall i \in [0..m].\openrule
          {
@@
          {s_{3i} \OTarrow {\tau} s_{3(i+1)}}\! \in\! \mathcal{T}
-\Big) \\       
-          \bigvee \Big(\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)\!  \implies\!  {
+\Big)  \implies\!  {
 \openrule
@@
 
- and similarly for $Pred_{4i}$, $Pred_{5i}$, $Pred_{4i}$, and $Pred_{4i}$  \TODO{define or OK this way?}
+ and similarly for $\Pred_{4i}$, $\Pred_{5i}$, $\Post_{4i}$, and $\Post_{5i}$  \TODO{define or OK this way?}
 
@@
      \land \alpha\!=\!\alpha_x \land  
-     \Pred_{s',t_x}\subst{\Post_{OT}\shortotimes\Post_{OT_x}}\right)}$
+     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}$
 
@@
      \land \alpha_x\!=\!\tau \land  
-     \Pred_{s_{11},t_x}\subst{\Post_1\shortotimes\Post_{OT_x}}\right)$
+     \Pred_{s_{11},t_x}\subst{\Post_1\uplus\Post_{OT_x}}\right)$
 
@@
  \!\!  \left( \forall j\in J_{x y}. \vis{\beta_{2j}}\!=\!\gamma_{jx y}\Rightarrow \Pred_{OT_{x y}}\!\land \alpha\!=\!\alpha_{x y} \land  
-     \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_{OT_{x y}}}\right)$
+     \Pred_{s_{21},t_{x y}}\subst{\Post_2\uplus\Post_{OT_{x y}}}\right)$
 
@@
      \land\! \alpha_{x y z}\!=\!\tau \land  
-     \Pred_{s_{31},t_{x y z}}\subst{\Post_3\shortotimes\Post_{OT_{x y z}}}\right)$
+     \Pred_{s_{31},t_{x y z}}\subst{\Post_3\uplus\Post_{OT_{x y z}}}\right)$
 
@@
      \land \alpha \!=\! \alpha_{x y}' \land  
-     \Pred_{s',t_{x y z}}\subst{\Post_{OT}\shortotimes\Post\,}\right)$
+     \Pred_{s',t_{x y z}}\subst{\Post_{OT}\uplus\Post\,}\right)$
 Let's start with the hypothesis we have:\\
@@
      \land \alpha_x\!=\!\tau \land  
-     \Pred_{s_{11},t_x}\subst{\Post_1\shortotimes\Post_{OT_x}}\right)$\\
+     \Pred_{s_{11},t_x}\subst{\Post_1\uplus\Post_{OT_x}}\right)$\\
 The conjunction of the term $\Pred_2\subst{\Post_1}$ with the both sides of the implication, we get:\\  
@@
      \land \alpha_x\!=\!\tau \land  
-     \Pred_{s_{11},t_x}\subst{\Post_1\shortotimes\Post_{OT_x}}\right) \wedge\Pred_2\subst{\Post_1\shortotimes\Post_{OT_x}}  \\
+     \Pred_{s_{11},t_x}\subst{\Post_1\uplus\Post_{OT_x}}\right) \wedge\Pred_2\subst{\Post_1\uplus\Post_{OT_x}}  \\
 $
-Note that  on the right side of the implication we added  the substitution  of $\Post_{OT_x}$ without affecting the validity of the statement, because of the domain independence of the substitution \TODO{l'argument ne me convainc pas}.
+Note that  on the right side of the implication we added  the substitution  of $\Post_{OT_x}$ without affecting the validity of the statement, because of the domain independence of the substitution.
 Hence a little rewriting gives:\\
@@
 \!\!   \left(\forall j\in J_x. \vis{\beta_{1j}}\!=\!\gamma_{jx}\Rightarrow \Pred_{OT_x}
-     \!\land\! \alpha_x\!=\!\tau\land(\Pred_{s_{11},t_x}\wedge\Pred_2)\subst{\Post_1\shortotimes\Post_{OT_x}} \right)$\\
+     \!\land\! \alpha_x\!=\!\tau\land(\Pred_{s_{11},t_x}\wedge\Pred_2)\subst{\Post_1\uplus\Post_{OT_x}} \right)$\\
 By replacing the inner sub-term $(\Pred_{s_{11},t_x}\wedge\Pred_2)$ by the conclusion of the  implication given in case 2,  the formula becomes: \\
@@
 \vis{\beta_{2j}}\!\!=\!\!\gamma_{jx y} \\ \Rightarrow \Pred_{OT_{x y}}\land \alpha\!=\!\alpha_{x y}\!
-\land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_{OT_{x y}}})\Big)\subst{\Post_1\shortotimes\Post_{OT_x}} \Big)$\\
+\land \Pred_{s_{21},t_{x y}}\subst{\Post_2\uplus\Post_{OT_{x y}}})\Big)\subst{\Post_1\uplus\Post_{OT_x}} \Big)$\\
 Furthermore, the rewriting of the formula  gives:\\
@@
 \vis{\beta_{1j}}\!\!=\!\!\gamma_{jx} \land  \forall j \in J_{x y}.
-\vis{\beta_{2j}}\subst{\Post_1\shortotimes\Post_{OT_x}} \!=\!\gamma_{jx y}  \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_1\shortotimes\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \subst{\Post_1\shortotimes\Post_{OT_x}} \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_1\shortotimes \Post_{OT_{x y}}\shortotimes \Post_{OT_x}}\Big)$\\
+\vis{\beta_{2j}}\subst{\Post_1\uplus\Post_{OT_x}} \!=\!\gamma_{jx y}  \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_1\uplus\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \subst{\Post_1\uplus\Post_{OT_x}} \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{x y}}\uplus \Post_{OT_x}}\Big)$\\
 As $Post_1$  does not act on $\gamma_{jx y}$, nor on $ \Pred_{OT_{x y}}$ and $  \alpha_{x y}$, the formula can be simplified as follows:\\
@@
 \vis{\beta_{1j}}\!=\!\gamma_{jx} \land  \forall j \in J_{x y}.
-\vis{\beta_{2j}}\subst{\Post_{OT_x}}\!=\!\gamma_{jx y}   \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \subst{\Post_{OT_x}} \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_1\shortotimes \Post_{OT_{x y}}\shortotimes \Post_{OT_x}}\Big)$\\
+\vis{\beta_{2j}}\subst{\Post_{OT_x}}\!=\!\gamma_{jx y}   \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \subst{\Post_{OT_x}} \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{x y}}\uplus \Post_{OT_x}}\Big)$\\
 Finally, the conjunction with the term $\Pred_3\subst{\Post_2\shortotimes\Post_1}$ of the both sides of the implication and rewriting, we get:\\

### 2019-05-07 2016-Weak-FH-Bisim/WeakBisim.tex
lemma 6

@@
 				\Post}
-			{\ostate{s_l^{l\in L}} \OTWeakarrow {\alpha}
+			{\ostate{s_l^{l\in L}} \OTWeakarrow {\alpha'}
 				\ostate{s_l'^{\, l\in L}}} 
 \end{mathpar}
-By Lemma \ref{lem-rel-OT-WOT} this implies the following \TODO{replace $\alpha$ by $\alpha'$}: \\			
+By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
 $ \forall p\! \in [0..m_1]\,		
@@
     {
-       \set{\beta^1_p},\Pred^1_p,\Post^1_p   }
+       \set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
          {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$,  $\qquad  P[Q]_{j_0}	\models \openrule
          {
-           \set{\beta^2},\Pred\,^2,\Post^2 }
+           \set{\beta_2},\Pred_2,\Post_2 }
          {\ostate{t_l^{l\in L}} \OTarrow {\alpha} \ostate{{t'}_l^{l\in L}}}
@@
          {
-           \set{\beta^3_p},\Pred\,^3_p, \Post_p^3   }
+           \set{\beta_{3p}},\Pred_{3p}, \Post_{3p}   }
          {\ostate{u^{l\in L}_{pl}} \OTarrow {\tau} \ostate{u^{l\in L}_{(p+1)l}}}
@@
 where for all $l\in L$:\\
+$\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}}$\\
 $s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
 $\displaystyle{
-\set{\gamma}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}\subst{\bigotimes_{j=i-1}^{0} \Post_j^1 } }  \dotcup  \vis{\set{\beta^2}\subst{\bigotimes_{j=n}^{0}\Post_j^1}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i} \subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=m_1}^{0}\Post^1_j} }}
+\set{\gamma}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!
+\Post_{1j}}}\dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }}
 \\
-\Pred=\bigwedge_{i=0}^{m_1}\Pred^1_i\subst{\bigotimes_{j=i-1}^{0}\Post_j^1}\land\Pred^2 \subst{\bigotimes_{j=m_1}^{0}\Post_j^1}\land\\ 
-~\qquad\quad\Big(\bigwedge_{i=0}^{m_2}\Pred_i^3\subst{\bigotimes_{j=i-1}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=m_1}^{0}\Post^1_j}\Big)\\
-\Post=\bigotimes_{j=m_2}^{0}\Post_j^3\shortotimes\Post^2\shortotimes\bigotimes_{j=m_1}^{0}\Post^1_j$
-
-------------------------
-
-$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta^1_i}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta^3_i}}}\\
-\Pred=\bigwedge_{i=0}^{m_1}\!\big(\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land \bigwedge_{i=0}^{m_2}\!\Pred_i^3\big(\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\big)\\
-\Post=\bigotimes_{i=0}^{m_2}\Post^3_i\subst{\Post^2}\bigotimes_{j=0}^{m_1}\subst{\Post^1_j}
-$\\
+\Pred=\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\land\\ 
+~\qquad\quad\bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
+\Post=\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}$\\
 
@@
     {
-       \set{\beta^1_p},\Pred^1_p,\Post^1_p   }
+       \set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
          {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$ \\
@@
 			{
-				(\beta^1_{pj})^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
-				{\Pred^{1a}_p},  
-				{\Post^{1a}_p}}
+				(\beta_{1pj})^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
+				{\Pred'_{1p}},  
+				{\Post'_{1p}}}
 			{\ostate{s_{p l}^{l\in L\setminus L_Q}} \OTarrow {\tau}
@@
 			{
-				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred^{1b}_p}},  
-				{{\Post^{1b}_p}}}
-				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha^1_{p}}
+				(\beta_{1pj})^{j\in J\cap\Holes(Q)}, {\Pred''_{1p}},  
+				{\Post''_{1p}}}
+				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{1p}}
 				\ostate{s_{(p+1)l}^{l\in L_Q}}}
@@
 $
-such that  $\Pred^1_p \iff {\Pred^{1a}_p}
-		\land {\Pred^{1b}_p}\land \alpha^1_p=\beta^1_{pj_0}$, $\Post^1_p={\Post^{1a}_p}\uplus 
-		{\Post^{1b}_p}$ where ${{\Post^{1b}_p}}$ is the restriction of $\Post^1_p$ over variables of $\Leaves(Q)$.\\
+such that  $\Pred_{1p} \iff {\Pred'_{1p}}
+		\land {\Pred''_{1p}}\land \alpha_{1p}=\beta_{1pj_0}$, $\Post_{1p}={\Post'_{1p}}\uplus 
+		{\Post''_{1p}}$ where ${{\Post''_{1p}}}$ is the restriction of $\Post_{1p}$ over variables of $\Leaves(Q)$.\\
 Else $Q$ does not move and we have: \\
@@
 			{
-				(\beta^1_{pj})^{j\in (J\setminus \Holes(Q)) }, 
-				{\Pred^{1a}_p},  
-				{\Post^{1a}_p}}
+				(\beta_{1pj})^{j\in (J\setminus \Holes(Q)) }, 
+				{\Pred'_{1p}},  
+				{\Post'_{1p}}}
 			{\ostate{(s_{p l})^{l\in L\setminus L_Q}} \OTarrow {\tau}
@@
          {
-           \set{\beta^2},\Pred^2,\Post^2 }
+           \set{\beta_2},\Pred_2,\Post_2 }
          {\ostate{t} \OTarrow {\alpha} \ostate{t'}}$\\
@@
 			{
-				(\beta^2_j)^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
-				{\Pred^{2a}},  
-				{\Post^{2a}}}
+				(\beta_{2j})^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
+				{\Pred'_2},  
+				{\Post'_2}}
 			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
@@
 			{
-				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {\Pred^{2b}},  
-				{\Post^{2b}}}
-			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha^2}
+				(\beta_{2j})^{j\in J\cap\Holes(Q)}, {\Pred''_2},  
+				{\Post''_2}}
+			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_2}
 				\ostate{t_l'^{\,l\in L_Q}}}
@@
 $\\
-such that  $\Pred^2 \iff {\Pred^{2a}}
-		\land {\Pred^{2b}}\land \alpha^2=\beta^2_{j_0}$, $\Post^2={\Post^{2a}}\uplus 
-		{\Post^{2b}}$ where ${\Post^{2b}}$ is the restriction of $\Post^2$ over variables of $\Leaves(Q)$.
+such that  $\Pred_2 \iff {\Pred'_2}
+		\land {\Pred''_2}\land \alpha_2=\beta_{2j_0}$, $\Post_2={\Post'_2}\uplus 
+		{\Post''_2}$ where ${\Post''_2}$ is the restriction of $\Post_2$ over variables of $\Leaves(Q)$.
 
@@
 where for all $l\in L$:\\
-$s_l=s_{0l} \wedge s_{(m_1+1)l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)l}=s'_l$\\
-$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\},
-\displaystyle{\gamma_j}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{ij}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{ij}}
-\\
-\Pred\,'=\big(\bigwedge_{i=0}^{m_1}
-{\Pred_i^{1a}}\bigotimes_{j=0}^{i-1}\subst{{\Post_j^{1a}}}\big)
-\land{\Pred^{2a}}\bigotimes_{i=0}^{m_1}\subst{{\Post_i^{1a}}}\land \\
-~~\qquad\quad\big(\bigwedge_{i=0}^{m_2}{\Pred_i^{3a}}\bigotimes_{j=0}^{i-1}\subst{{\Post_j^{3a}}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}}\big)\\
-\Post'=\bigotimes_{i=0}^{m_2}{\Post_i^{3a}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}}
-$
+$\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}}$\\
+$s_l=s_{0l} \wedge s_{(m_1+1)l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)l}=s'_l$
+$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\}$,\\
+$\set{\gamma}_j=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1ij}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}}\dotcup  \vis{\set{\beta_{2j}}\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}} \dotcup\\
+~~\qquad \mybigdotcup_{i=0}^{m_2}
+\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}} }\\
+\Pred\,'=\bigwedge_{i=0}^{m_1}\Pred'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}\land\Pred'_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}\land\\ 
+~\qquad\qquad\bigwedge_{i=0}^{m_2}\Pred'_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}\\
+\Post'=\bigotimes_{j=m_2}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}$
 
@@
 			{
-				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^{1b}}},  
-				{{\Post_p^{1b}}}}
-				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha^1_{p}}
+				(\beta_{1pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_{1p}}},  
+				{{\Post''_{1p}}}}
+				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{1p}}
 				\ostate{s_{(p+1)l}^{l\in L_Q}}}
@@
 			{
-				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {\Pred^{2b}},  
-				{\Post^{2b}}}
-			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha^2}
+				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {\Pred''_2},  
+				{\Post''_2}}
+			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_2}
 				\ostate{t_l'^{\,l\in L_Q}}}
@@
 			{
-				(\beta^3_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^{3b}}},  
-				{{\Post_p^{3b}}}}
-				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha^3_{p}}
+				(\beta_{3pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_{3p}}},  
+				{{\Post''_{3p}}}}
+				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha_{3p}}
 				\ostate{u_{(p+1)l}^{l\in L_Q}}}
@@
 			{
-				(\beta_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^b}},  
-				{{\Post_p^b}}}
+				(\beta_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_p}},  
+				{{\Post''_p}}}
 				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
@@
 We can decompose each of the $n$ subsequences; the length of the subsequence number $k$ is $n_k$,  and the subsequence is made of the following OTs:\\
-$\forall p\! \in\! [0..(n_k'\!-\!1)] Q\models{\openrule
-			{
-				(\beta^1_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^{1b}}},  
-				{{\Post_p^{1b}}}}
+$\forall p\! \in\! [0..(n_k\!-\!1)] Q\models{\openrule
+			{
+				(\beta_{1pj})^{j\in J\cap\Holes(Q)}, {{\Pred''{1p}}},  
+				{{\Post''_{1p}}}}
 				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
@@
 			{
-				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred^{2b}}},  
-				{{\Post^{2b}}}}
-				{\ostate{v_{n_k'l}^{l\in L_Q}} \OTarrow {\alpha'_k}
+				(\beta_{2j})^{j\in J\cap\Holes(Q)}, {{\Pred''_2}},  
+				{{\Post''_2}}}
+				{\ostate{v_{n_k'l}^{l\in L_Q}} \OTarrow {\alpha_k}
 				\ostate{v_{(n_k'+1)l}^{l\in L_Q}}}
@@
 and
-$\forall p \in [(n_k'\!+\!1)..(n_k\!-\!1)]\,\, Q\models{\openrule
-			{
-				(\beta^3_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^{3b}}},  
-				{{\Post_p^{3b}}}}
+$\forall p \in [(n_k\!+\!1)..(n_k'\!-\!1)]\,\, Q\models{\openrule
+			{
+				(\beta^3_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_{3p}}},  
+				{{\Post''_{3p}}}}
 				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
@@
 \end{mathpar}
-$\forall l \in L_Q. v_l=v_{0l} \wedge v_l'=v_{n_kl}$\\
-$\forall j \in  (J\cap\Holes(Q)),\,
-\displaystyle{\gamma_{kj} }=\mybigdotcup_{i=0}^{(n_k'-1)}\!\!\vis{\beta^1_{ij}}\,\dotcup\,\vis{\set{\beta^2_j}}\,\dotcup\!\!\!\mybigdotcup_{i=(n_k'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij}}
-\\
-\Pred_k=\Big(\!\!\!\bigwedge_{i=0}^{(n_k'-1)}\!\!
-{\Pred_i^{1b}}\bigotimes_{j=0}^{(i-1)}\subst{{\Post_j^{1b}}}\Big)
-\land\Big({\Pred^{2b}}\bigotimes_{i=0}^{(n_k'-1)}\subst{{\Post_i^{1b}}}\Big)\land\\
-~\qquad\qquad\Big(\!\!\!\bigwedge_{i=(n_k'+1)}^{(n_k-1)}\!\!\!{\Pred_i^{3b}}\bigotimes_{j=n_k'+1}^{(i-1)}\subst{{\Post_j^{3b}}}\subst{{\Post^{2b}}}\bigotimes_{i=0}^{(n_k'-1)}\subst{{\Post_i^{1b}}}\Big)\\
-\Post_k=\bigotimes_{i=(n_k'+1)}^{(n_k-1)}\!\!\!{\Post_i^{3b}}\Big(\subst{{\Post^{2b}}}\bigotimes_{i=0}^{(n_k'-1)}\subst{{\Post_i^{1b}}}\Big)
-$\\
+$\alpha_k'=\alpha_k\displaystyle{\subst{\bigotimes_{j=0}^{(n_k-1)}\!\!\Post''_{1j}}}$\\
+$\forall l \in L_Q. v_l=v_{0l} \wedge v_l'=v_{n_kl}$, 
+$\forall j \in  (J\cap\Holes(Q)),\,$\\
+$\displaystyle{\gamma_{kj} }=\displaystyle{\mybigdotcup_{i=0}^{n_k-1} \vis{\set{\beta_{1ij}}\subst{\bigotimes_{j=i-1}^{0}\!\!\!\Post''_{1j}}}\dotcup \vis{\set{\beta_{2j}}\subst{\bigotimes_{j=n_k-1}^{0}\!\!\!\Post''_{1j}}}} \dotcup\\
+~~\qquad \mybigdotcup_{i=n_k+1}^{n_k'-1}
+\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=n_k-1}^{0}\!\!\!\Post''_{1j}} }\\
+\Pred_k=\bigwedge_{i=0}^{n_k-1}\!\!\Pred''_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred''_2 \subst{\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{1j}}\land\\ 
+~\qquad\quad\bigwedge_{i=n_k+1}^{n_k'-1}\!\!\!\Pred''_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=n_k-1}^{0}\!\!\!\Post''_{1j}}\\
+\Post_k= \bigotimes_{j=n_k'-1}^{0}\!\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{1j}$\\
 
@@
 might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.\\
-
 We have: 
-$\displaystyle{\gamma_{j_0}}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{i{j_0}}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{i{j_0}}}$
-
-Additionally, we have
+$\displaystyle{\gamma_{j_0}}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta_{1i{j_0}}} \dotcup  \vis{\set{\beta_{2i}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3i{j_0}}}$. Additionally, we have
 $[\alpha'_0..
@@
 We have:\\
-$\Pred=\displaystyle{\bigwedge_{i=0}^{m_1}\!\big(\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land \bigwedge_{i=0}^{m_2}\!\Pred_i^3\big(\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}}\big)$\\
-By replacing ${\Pred^{1}_i}$,  $\Pred^2$, and ${\Pred^{3}_i}$ by their equivalent formula  we obtain:\\
-$\Pred \iff\displaystyle{\bigwedge_{i=0}^{m_1}({\Pred^{1a}_i}
-		\land {\Pred^{1b}_i}\land \alpha^1_i=\beta^1_{ij_0}) \bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land}\\
-~~\qquad\qquad\qquad({\Pred^{2a}}\land {\Pred^{2b}}\land \alpha^2=\beta^2_{j_0})	\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land\\
-~~\qquad\qquad\bigwedge_{i=0}^{m_2} ({\Pred^{3a}_i}\land {\Pred^{3b}_i}\land \alpha^3_i=\beta^3_{ij_0})\big(\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\big)$\\
+$\Pred=\displaystyle{\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\land 
+\bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}}$\\
+By replacing $\Pred_{1i}$,  $\Pred_2$, and $\Pred_{3i}$ by their equivalent formula  we obtain:\\
+$\Pred \iff\displaystyle{\bigwedge_{i=0}^{m_1}({\Pred'_{1i}}
+		\land {\Pred''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}) \bigotimes_{j=0}^{i-1}\subst{\Post_{1j}}\land}\\
+~~\qquad\qquad\qquad({\Pred'_2}\land {\Pred''_2}\land \alpha_2=\beta_{2j_0})	\bigotimes_{i=0}^{m_1}\subst{\Post_{1i}}\land\\
+~~\qquad\qquad\bigwedge_{i=0}^{m_2} ({\Pred'_{3i}}\land {\Pred''_{3i}}\land \alpha_{3i}=\beta_{3ij_0})
+\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}$\\
 By distribution of the substitution operation over the logical operator we can deduce:\\
 $\Pred\iff \displaystyle{\big(\bigwedge_{i=0}^{m_1}
-{\Pred_i^{1a}}\bigotimes_{j=0}^{i-1}\subst{{\Post_j^{1a}}}\big)
-\land{\Pred^{2a}}\bigotimes_{i=0}^{m_1}\subst{{\Post_i^{1a}}}\land} \\
-~~\qquad\qquad\quad\big(\bigwedge_{i=0}^{m_2}{\Pred_i^{3a}}\bigotimes_{j=0}^{i-1}\subst{{\Post_j^{3a}}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}}\big) \land\\	
-~\qquad\qquad\quad\bigwedge_{i=0}^{m_1}({\Pred^{1b}_i}\land \alpha^1_i=\beta^1_{ij_0}) \bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\land({\Pred^{2b}}\land \alpha^2=\beta^2_{j_0})	\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land\\
-~\qquad\qquad\quad\bigwedge_{i=0}^{m_2} ({\Pred^{3b}_i}\land \alpha^3_i=\beta^3_{ij_0})\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}
+{\Pred'_{1i}}\bigotimes_{j=0}^{i-1}\subst{{\Post'_{1j}}}\big)
+\land{\Pred'_2}\bigotimes_{i=0}^{m_1}\subst{{\Post'_{1i}}}\land} \\
+~~\qquad\qquad\quad\big(\bigwedge_{i=0}^{m_2}{\Pred'_{3i}}\bigotimes_{j=0}^{i-1}\subst{{\Post'_{3j}}}\subst{{\Post'_2}}\bigotimes_{j=0}^{m_1}\subst{{\Post'_{1j}}}\big) \land\\	
+~\qquad\qquad\quad\bigwedge_{i=0}^{m_1}({\Pred''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}) \bigotimes_{j=0}^{i-1}\subst{\Post_{1j}}\land({\Pred''_2}\land \alpha_2=\beta_{2j_0})	\bigotimes_{i=0}^{m_1}\subst{\Post_{1i}}\land\\
+~\qquad\qquad\quad\bigwedge_{i=0}^{m_2} ({\Pred''_{3i}}\land \alpha_{3i}=\beta_{3ij_0})\bigotimes_{j=0}^{i-1}\subst{\Post_{3j}}\subst{\Post_2}  \bigotimes_{i=0}^{m_1}\subst{\Post_{1i}}
 $\\		
@@
 Concerning the postcondition we have:\\
-$\Post=\displaystyle{\bigotimes_{i=0}^{m_2}\Post^3_i\subst{\Post^2}\bigotimes_{j=0}^{m_1}\subst{\Post^1_j}}$\\
-By replacing ${\Post^{1}_i}$,  $\Post^2$, and ${\Post^{3}_j}$ and because the ${\Post_i^{ja}}$ and ${\Post_i^{jb}}$ are independent (the ${\Post_i^{ja}}$ concern the leaves of $P$ while the ${\Post_i^{jb}}$ concern the leaves of $Q$), we obtain:\\
-$\Post= \displaystyle{\bigotimes_{i=0}^{m_2}\subst{{\Post^{3a}_i}\uplus 
-		{\Post^{3b}_i}} \subst{{\Post^{2a}}\uplus 
-		{\Post^{2b}}} \bigotimes_{j=0}^{m_1}\subst{ {\Post^{1a}_i}\uplus 
-		{\Post^{1b}_i}}}\\
-~~\qquad= \bigotimes_{i=0}^{m_2}{\Post_i^{3a}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}} \uplus \bigotimes_{i=0}^{m_2}{\Post_i^{3b}}\subst{{\Post^{2b}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1b}}} \\
+$\Post=\displaystyle{\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}$\\
+By replacing ${\Post_{1i}}$,  $\Post_2$, and ${\Post_{3i}}$ and because the ${\Post'_i}$ and ${\Post''_i}$ are independent (the ${\Post'_i}$ concern the leaves of $P$ while the ${\Post''_i}$ concern the leaves of $Q$), we obtain:\\
+$\Post= \displaystyle{\bigotimes_{i=0}^{m_2}\subst{{\Post'_{3i}}\uplus 
+		{\Post''_{3i}}} \subst{{\Post'_2}\uplus 
+		{\Post''_2}} \bigotimes_{j=0}^{m_1}\subst{ {\Post'_{1i}}\uplus 
+		{\Post''_{1i}}}}\\
+~~\qquad= \bigotimes_{i=0}^{m_2}{\Post'_{3i}}\subst{{\Post'_2}}\bigotimes_{j=0}^{m_1}\subst{{\Post'_{1j}}} \uplus \bigotimes_{i=0}^{m_2}{\Post''_{3i}}\subst{{\Post''_2}}\bigotimes_{j=0}^{m_1}\subst{{\Post''_{1j}}} \\
 ~~\qquad= \Post' \uplus \bigotimes_{j=0}^{n} \Post_j $\\

### 2019-05-09 2016-Weak-FH-Bisim/WeakBisim.tex
corrections notations

@@
 \end{mathpar}
-For each of the weak open transition obtained above, we have  $(s_{11},t_x|\Pred_{s_{11},t_x})\in \mathcal{R}$  and $s_{11}=s_{20}$, so we have  $(s_{20},t_x|\Pred_{s_{20},t_x})\in \mathcal{R}$.
-Again
+For each  weak open transition obtained above, we have  $(s_{11},t_x|\Pred_{s_{11},t_x})\in \mathcal{R}$  and $s_{11}=s_{20}$, so we have  $(s_{20},t_x|\Pred_{s_{20},t_x})\in \mathcal{R}$. Again 
  by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{x y}^{x\in X,y\in Y} \subseteq \WT_2$:
@@
      \!\land\! \alpha_x\!=\!\tau \land\Big(\displaystyle{\bigvee_{y\in Y}}
-   ( \forall j\in J_{x y}.
+    \forall j\in J_{x y}.
 \vis{\beta_{2j}}\!\!=\!\!\gamma_{jx y} \\ \Rightarrow \Pred_{OT_{x y}}\land \alpha\!=\!\alpha_{x y}\!
-\land \Pred_{s_{21},t_{x y}}\subst{\Post_2\uplus\Post_{OT_{x y}}})\Big)\subst{\Post_1\uplus\Post_{OT_x}} \Big)$\\
-Furthermore, the rewriting of the formula  gives:\\
+\land \Pred_{s_{21},t_{x y}}\subst{\Post_2\uplus\Post_{OT_{x y}}}\Big)\subst{\Post_1\uplus\Post_{OT_x}} \Big)$\\
+Furthermore, the rewriting of the formula  gives \TODO{ajouter argument $\alpha\!=\!\alpha_{x y} \subst{\Post_1\uplus\Post_{OT_x}}$ et $\vis{\beta_{2j}}\subst{\Post_1\uplus\Post_{OT_x}} \!=\!\gamma_{jx y}$}:\\
 $(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
@@
 \vis{\beta_{1j}}\!\!=\!\!\gamma_{jx} \land  \forall j \in J_{x y}.
-\vis{\beta_{2j}}\subst{\Post_1\uplus\Post_{OT_x}} \!=\!\gamma_{jx y}  \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_1\uplus\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \subst{\Post_1\uplus\Post_{OT_x}} \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{x y}}\uplus \Post_{OT_x}}\Big)$\\
+\vis{\beta_{2j}}\subst{\Post_1\uplus\Post_{OT_x}} \!=\!\gamma_{jx y}  \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_1\uplus\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \subst{\Post_1\uplus\Post_{OT_x}} \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{x y}}\shortotimes \Post_{OT_x}}\Big)$\\
 As $Post_1$  does not act on $\gamma_{jx y}$, nor on $ \Pred_{OT_{x y}}$ and $  \alpha_{x y}$, the formula can be simplified as follows:\\
@@
 \vis{\beta_{1j}}\!=\!\gamma_{jx} \land  \forall j \in J_{x y}.
-\vis{\beta_{2j}}\subst{\Post_{OT_x}}\!=\!\gamma_{jx y}   \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \subst{\Post_{OT_x}} \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{x y}}\uplus \Post_{OT_x}}\Big)$\\
+\vis{\beta_{2j}}\subst{\Post_{OT_x}}\!=\!\gamma_{jx y}   \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \subst{\Post_{OT_x}} \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{x y}}\shortotimes \Post_{OT_x}}\Big)$\\
 Finally, the conjunction with the term $\Pred_3\subst{\Post_2\shortotimes\Post_1}$ of the both sides of the implication and rewriting, we get:\\
@@
 \vis{\beta_{2j}}\subst{\Post_{OT_x}} \!=\!\gamma_{jx y} \Rightarrow \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \alpha_x\!=\!
-\tau \land \alpha\!=\! \alpha_{x y} \subst{\Post_{OT_x}} \land (\Pred_{s_{21},t_{xy}} \land  \Pred_3) \subst{\Post_2\shortotimes \Post_1\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$\\ 
+\tau \land \alpha\!=\! \alpha_{x y} \subst{\Post_{OT_x}} \land (\Pred_{s_{21},t_{xy}} \land  \Pred_3) \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$\\ 
 Again note that because of the domain independence of the substitution, we removed $\Post_1$ and  we  added  $\Post_{OT_{x y}}\shortotimes\,\Post_{OT_x}$ on the right side of the implication.\\
@@
   \Pred_{OT_{x y z}}\!\subst{\Post_{OT_{x y}}\shortotimes\,\Post_{OT_x}} \land \alpha_x\!=\!
-\tau \!\land \alpha\!=\!\alpha_{x y} \subst{\Post_{OT_x}}\land \alpha_{x y z}\!=\!\tau \land \Pred_{s_{31},t_{x y z}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\shortotimes \,\Post_{OT_{x y z}}\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$\\
+\tau \!\land \alpha\!=\!\alpha_{x y} \subst{\Post_{OT_x}}\land \alpha_{x y z}\!=\!\tau \land \Pred_{s_{31},t_{x y z}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{x y z}}\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}}_{\Post}} \Big)$\\
 Having $s_{31}=s'$ we can conclude:\\
-$(\Pred_{s,t} \land \Pred_1)\land \Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\\
+$\Pred_{s,t} \land \Pred_{OT}\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} \displaystyle{\bigvee_{z\in Z}} 
-\Big(\forall j\in J_{x y z}.
-\vis{\beta^1_j}.\vis{\beta_{2j}}\subst{\Post_{OT_x}}.\vis{\beta_{3j}}\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \!=\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \land \alpha\!=\!\alpha_{x y}\subst{\Post_{OT_x}} \land \Pred_{s',t_{x y z}}\subst{\Post_{OT}\shortotimes\Post_{OT_{x y z}}\shortotimes\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$\\
- \TODO{gamma ne me convainc pas et je dois generaliser}
-This is exactly what we needed to prove. \qed
+\Big(\forall j\in J_{x y z}. \gamma_j =\gamma_{j x y z} \Rightarrow  \Pred \land \alpha =\alpha_{x y}\subst{\Post_{OT_x}} \land \Pred_{s',t_{x y z}}\subst{\Post_{OT}\uplus \Post} \Big)$\\
+ This is exactly what we needed to prove \TODO{je dois generaliser}. \qed
 \end{proof}

### 2019-05-09 2016-Weak-FH-Bisim/WeakBisim.tex
skype call

@@
 \end{definition}
+
+Another consequence of the semantics and logical interpretation of the formulas is that we make no distinction between the equality and the equivalence on boolean formulas, i.e.
+equivalence of two predicates $\Pred$ and $\Pred\,'$ can be denoted $\Pred=\Pred\,'$.
 
@@
 
-For the sake of simplicity, we will  restrict $n$ and $m$ to be equal to $1$, hence a single tau open transition will be considered; however the proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule.
+For the sake of simplicity, we prove the rule in the  restricted case where $n$ and $m$ to be equal to $1$, hence a single tau open transition will be considered on each side of the potentially visible one.
+The proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule.
 Consider each open transition separately:
@@
 \vis{\beta_{1j}}\!\!=\!\!\gamma_{jx} \land  \forall j \in J_{x y}.
-\vis{\beta_{2j}}\subst{\Post_1\uplus\Post_{OT_x}} \!=\!\gamma_{jx y}  \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_1\uplus\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \subst{\Post_1\uplus\Post_{OT_x}} \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{x y}}\shortotimes \Post_{OT_x}}\Big)$\\
+\vis{\beta_{2j}}\subst{\Post_1\uplus\Post_{OT_x}} \!=\!\gamma_{jx y}  \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_1\uplus\Post_{OT_x}} \land \alpha_x\!=\!\tau \land (\alpha\!=\!\alpha_{x y}) \subst{\Post_1\uplus\Post_{OT_x}} \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{x y}}\shortotimes \Post_{OT_x}}\Big)$\\
 As $Post_1$  does not act on $\gamma_{jx y}$, nor on $ \Pred_{OT_{x y}}$ and $  \alpha_{x y}$, the formula can be simplified as follows:\\
@@
  \text{and\qquad} \forall j\in J_p,\,\gamma_j= \mybigdotcup_{p=0}^n \gamma_{p j} \\
- \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred \iff \Pred\,'
+ \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred = \Pred\,'
 		\land \!\!\bigwedge_{p=0}^n((\alpha_p= \beta_p\land \Pred_p)\bigotimes_{i=0}^{p-1}\Post_i) 
@@
 and $\displaystyle{\bigcup_{p=0}^nJ_{p}} = J\cap\Holes(Q)$, $\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}}$, $\forall l\in L_Q,\, s_{0l}=s_l$, $s_{(n+1)l}=s'_l$  \\
-  $\Pred \iff \Pred\,'
-		\land \displaystyle{\bigwedge_{p=0}^n}((\alpha_p= \beta_{pj_0}\land \Pred_p)\bigotimes_{i=0}^{p-1}\Post_i),\text{and~}$\\
-$\displaystyle{\Post=\Post\,'\uplus\bigotimes_{p=0}^n
+  $\Pred = \Pred\,'
+		\land \displaystyle{\bigwedge_{p=0}^n}((\alpha_p= \beta_{pj_0}\land \Pred_p)\bigotimes_{i=p-1}^{0}\Post_i),\text{and~}$\\
+$\displaystyle{\Post=\Post\,'\uplus\bigotimes_{p=n}^0
 		\Post_p}$  \\
@@
 By replacing $\Pred_{1i}$,  $\Pred_2$, and $\Pred_{3i}$ by their equivalent formula  we obtain:\\
-$\Pred \iff\displaystyle{\bigwedge_{i=0}^{m_1}({\Pred'_{1i}}
-		\land {\Pred''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}) \bigotimes_{j=0}^{i-1}\subst{\Post_{1j}}\land}\\
-~~\qquad\qquad\qquad({\Pred'_2}\land {\Pred''_2}\land \alpha_2=\beta_{2j_0})	\bigotimes_{i=0}^{m_1}\subst{\Post_{1i}}\land\\
+$\Pred =\displaystyle{\bigwedge_{i=0}^{m_1}({\Pred'_{1i}}
+		\land {\Pred''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}) \bigotimes_{j=i-1}^{0}\subst{\Post_{1j}}\land}\\
+~~\qquad\qquad\qquad({\Pred'_2}\land {\Pred''_2}\land \alpha_2=\beta_{2j_0})	\bigotimes_{i=m_1}^{0}\subst{\Post_{1i}}\land\\
 ~~\qquad\qquad\bigwedge_{i=0}^{m_2} ({\Pred'_{3i}}\land {\Pred''_{3i}}\land \alpha_{3i}=\beta_{3ij_0})
@@
 By distribution of the substitution operation over the logical operator we can deduce:\\
-$\Pred\iff \displaystyle{\big(\bigwedge_{i=0}^{m_1}
-{\Pred'_{1i}}\bigotimes_{j=0}^{i-1}\subst{{\Post'_{1j}}}\big)
-\land{\Pred'_2}\bigotimes_{i=0}^{m_1}\subst{{\Post'_{1i}}}\land} \\
-~~\qquad\qquad\quad\big(\bigwedge_{i=0}^{m_2}{\Pred'_{3i}}\bigotimes_{j=0}^{i-1}\subst{{\Post'_{3j}}}\subst{{\Post'_2}}\bigotimes_{j=0}^{m_1}\subst{{\Post'_{1j}}}\big) \land\\	
-~\qquad\qquad\quad\bigwedge_{i=0}^{m_1}({\Pred''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}) \bigotimes_{j=0}^{i-1}\subst{\Post_{1j}}\land({\Pred''_2}\land \alpha_2=\beta_{2j_0})	\bigotimes_{i=0}^{m_1}\subst{\Post_{1i}}\land\\
-~\qquad\qquad\quad\bigwedge_{i=0}^{m_2} ({\Pred''_{3i}}\land \alpha_{3i}=\beta_{3ij_0})\bigotimes_{j=0}^{i-1}\subst{\Post_{3j}}\subst{\Post_2}  \bigotimes_{i=0}^{m_1}\subst{\Post_{1i}}
+$\Pred= \displaystyle{\big(\bigwedge_{i=0}^{m_1}
+{\Pred'_{1i}}\bigotimes_{j=i-1}^{0}\subst{{\Post'_{1j}}}\big)
+\land{\Pred'_2}\bigotimes_{i=m_1}^{0}\subst{{\Post'_{1i}}}\land} \\
+~~\qquad\qquad\quad\big(\bigwedge_{i=0}^{m_2}{\Pred'_{3i}}\bigotimes_{j=i-1}^{0}\subst{{\Post'_{3j}}}\subst{{\Post'_2}}\bigotimes_{j=m_1}^{0}\subst{{\Post'_{1j}}}\big) \land\\	
+~\qquad\qquad\quad\bigwedge_{i=0}^{m_1}({\Pred''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}) \bigotimes_{j=i-1}^{0}\subst{\Post_{1j}}\land({\Pred''_2}\land \alpha_2=\beta_{2j_0})	\bigotimes_{i=m_1}^{0}\subst{\Post_{1i}}\land\\
+~\qquad\qquad\quad\bigwedge_{i=0}^{m_2} ({\Pred''_{3i}}\land \alpha_{3i}=\beta_{3ij_0})\bigotimes_{j=i-1}^{0}\subst{\Post_{3j}}\subst{\Post_2}  \bigotimes_{i=m_1}^{0}\subst{\Post_{1i}}
 $\\		
 Therefore, we have:\\
-$\Pred\iff \Pred\,' \wedge \displaystyle{\bigwedge_{p=0}^{n}}((\alpha_p= \beta_{pj_0}\land \Pred_p)\bigotimes_{i=0}^{p-1}\Post_i)$\\ where $n=m_1+m_2+1$	\\
+$\Pred= \Pred\,' \wedge \displaystyle{\bigwedge_{p=0}^{n}}((\alpha_p= \beta_{pj_0}\land \Pred_p)\bigotimes_{i=p-1}^{0}\Post_i)$\\ where $n=m_1+m_2+1$	\\
 Concerning the postcondition we have:\\
@@
 By replacing ${\Post_{1i}}$,  $\Post_2$, and ${\Post_{3i}}$ and because the ${\Post'_i}$ and ${\Post''_i}$ are independent (the ${\Post'_i}$ concern the leaves of $P$ while the ${\Post''_i}$ concern the leaves of $Q$), we obtain:\\
-$\Post= \displaystyle{\bigotimes_{i=0}^{m_2}\subst{{\Post'_{3i}}\uplus 
+$\Post= \displaystyle{\bigotimes_{i=m_2}^{0}\subst{{\Post'_{3i}}\uplus 
 		{\Post''_{3i}}} \subst{{\Post'_2}\uplus 
-		{\Post''_2}} \bigotimes_{j=0}^{m_1}\subst{ {\Post'_{1i}}\uplus 
+		{\Post''_2}} \bigotimes_{j=m_1}^{0}\subst{ {\Post'_{1i}}\uplus 
 		{\Post''_{1i}}}}\\
-~~\qquad= \bigotimes_{i=0}^{m_2}{\Post'_{3i}}\subst{{\Post'_2}}\bigotimes_{j=0}^{m_1}\subst{{\Post'_{1j}}} \uplus \bigotimes_{i=0}^{m_2}{\Post''_{3i}}\subst{{\Post''_2}}\bigotimes_{j=0}^{m_1}\subst{{\Post''_{1j}}} \\
-~~\qquad= \Post' \uplus \bigotimes_{j=0}^{n} \Post_j $\\
+~~\qquad= \bigotimes_{i=m_2}^{0}{\Post'_{3i}}\subst{{\Post'_2}}\bigotimes_{j=m_1}^{0}\subst{{\Post'_{1j}}} \uplus \bigotimes_{i=m_2}^{0}{\Post''_{3i}}\subst{{\Post''_2}}\bigotimes_{j=m_1}^{0}\subst{{\Post''_{1j}}} \\
+~~\qquad= \Post' \uplus \bigotimes_{j=n}^{0} \Post_j $\\
  where $n=m_1+m_2+1$	

### 2019-05-13 2016-Weak-FH-Bisim/WeakBisim.tex
notations

@@
 $
-\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\Post_j^1}}\\
+\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\!\!\Post_j^1}}\\
 s''=s_{10} \wedge s_{1(n+2)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
@@
            \beta_{2j}^{j\in J_2'},\Pred_2,\Post_2 }
-         {s_{20} \OTarrow {\alpha} s_{21}} \in \mathcal{T}_1
+         {s_{20} \OTarrow {\alpha'} s_{21}} \in \mathcal{T}_1
  \wedge
@@
 $
+\displaystyle{\alpha=\alpha'\subst{\bigotimes_{j=n}^{0}\Post_{1j}}}\\
 s=s_{10} \wedge s_{1(n+1)}=s_{20} \wedge s_{21} = s_{30} \wedge s_{3(m+1)}=s'\\
@@
 \end{mathpar}
-we have $(s,t|\Pred_{s,t})\in\mathcal{R}$ by hypothesis, and $s=s_{10}$ the we have $(s_{10},t|\Pred_{s_{10},t})\in\mathcal{R}$.
+we have $(s,t|\Pred_{s,t})\in\mathcal{R}$ by hypothesis and $s=s_{10}$.
 Thus, by  Definition \ref{def-Weak-bisim} we  can deduce there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
@@
            \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {t \OTWeakarrow {\alpha_x} t_x}
+         {u \OTWeakarrow {\alpha_x} u_x}
 \end{mathpar}
- such that  $\forall x,J_{x}=\{j\in J_1'|\beta_{1j}\neq\tau\}, (s_{11},t_x|\Pred_{s_{11},t_x})\in \mathcal{R}$. \\
+ such that  $\forall x,J_{x}=\{j\in J_1'|\beta_{1j}\neq\tau\}, u=t,  (s_{11},t_x|\Pred_{s_{11},u_x})\in \mathcal{R}$ and \\
  $\Pred_{s,t} \land \Pred_1\\
@@
      \land \alpha_x\!=\!\tau \land  
-     \Pred_{s_{11},t_x}\subst{\Post_1\uplus\Post_{OT_x}}\right)$
+     \Pred_{s_{11},u_x}\subst{\Post_1\uplus\Post_{OT_x}}\right)$
 
@@
            \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {t \OTWeakarrow {\tau} t_x}
+         {u \OTWeakarrow {\tau} u_x}
 \end{mathpar}
-\item Concerning the middle open transition in $\mathcal{T}_1$, we have:
+\item Concerning the middle open transition in $\mathcal{T}_1$:
  \begin{mathpar}
@@
 \end{mathpar}
-For each  weak open transition obtained above, we have  $(s_{11},t_x|\Pred_{s_{11},t_x})\in \mathcal{R}$  and $s_{11}=s_{20}$, so we have  $(s_{20},t_x|\Pred_{s_{20},t_x})\in \mathcal{R}$. Again 
- by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{x y}^{x\in X,y\in Y} \subseteq \WT_2$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j x y}^{j\in J_{x y}}, \Pred_{OT_{x y}},\Post_{OT_{x y}}}
-         {t_x \OTWeakarrow {\alpha_{x y}} t_{x y}}
+we have  $(s_{11},u_x|\Pred_{s_{11},u_x})\in \mathcal{R}$  and $s_{11}=s_{20}$. Again 
+ by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{y}^{y\in Y} \subseteq \WT_2$:
+ \begin{mathpar}
+    \openrule
+         {
+           \gamma_{y}^{j\in J_{y}}, \Pred_{OT_{y}},\Post_{OT_{y}}}
+         {u_x \OTWeakarrow {\alpha_{y}} v_{y}}
 \end{mathpar}
- such that  $\forall x,\forall y, J_{xy}=\{j\in J_2'|\beta_{2j}\neq\tau\}, 
-(s_{21},t_{x y}|\Pred_{s_{21},t_{x y}})\in \mathcal{R}$; \\
- $\Pred_{s_{11},t_x} \land \Pred_2\\
+ such that  $\forall y, J_{y}=\{j\in J_2'|\beta_{2j}\neq\tau\}, 
+(s_{21},v_{y}|\Pred_{s_{21},v_{y}})\in \mathcal{R}$; \\
+ $\Pred_{s_{11},u_x} \land \Pred_2\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}}
- \!\!  \left( \forall j\in J_{x y}. \vis{\beta_{2j}}\!=\!\gamma_{jx y}\Rightarrow \Pred_{OT_{x y}}\!\land \alpha\!=\!\alpha_{x y} \land  
-     \Pred_{s_{21},t_{x y}}\subst{\Post_2\uplus\Post_{OT_{x y}}}\right)$
+ \!\!  \left( \forall j\in J_{y}. \vis{\beta_{2j}}\!=\!\gamma_{jy}\Rightarrow \Pred_{OT_{y}}\!\land \alpha\!=\!\alpha_{y} \land  
+     \Pred_{s_{21},v_{y}}\subst{\Post_2\uplus\Post_{OT_{y}}}\right)$
 
@@
 \end{mathpar}
-From previous case, we have $(s_{21},t_{x y}|\Pred_{s_{21},t_{x y}})\in \mathcal{R}$, and we have $s_{21}=s_{30}$ then we have $(s_{30},t_{x y}|\Pred_{s_{30},t_{x y}})\in \mathcal{R}$. By
- Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{x y z}^{x\in X,y\in Y,z\in Z} \subseteq \WT_2$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j x y z}^{j\in J_{x y z}}, \Pred_{OT_{x y z}},\Post_{OT_{x y z}}}
-         {t_{x y} \OTWeakarrow {\alpha_{x y z}} t_{x y z}}
+From previous case, we have $(s_{21},v_{y}|\Pred_{s_{21},v_{y}})\in \mathcal{R}$, and we have $s_{21}=s_{30}$. Then, by
+ Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{x}^{z\in Z} \subseteq \WT_2$:
+ \begin{mathpar}
+    \openrule
+         {
+           \gamma_{jz}^{j\in J_{z}}, \Pred_{OT_{z}},\Post_{OT_{z}}}
+         {v_{y} \OTWeakarrow {\tau} w_{z}}
 \end{mathpar}
- such that  $\forall x, \forall y, \forall z,J_{xyz}= \{j\in J_3'|\beta_{3j}\neq\tau\}, 
-(s_{31},t_{x y z}|\Pred_{s_{31},t_{x y z}})\in \mathcal{R}$. \\
- $\Pred_{s_{21},t_{x y}} \land \Pred_3\\
+ such that  $\forall z, J_{z}= \{j\in J_3'|\beta_{3j}\neq\tau\}, 
+(s_{31},w_{z}|\Pred_{s_{31},w_{z}})\in \mathcal{R}$,  $w_z=t_x$ and \\
+ $\Pred_{s_{21},v_{y}} \land \Pred_3\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{z\in Z}}
-   \!\left( \forall j\in J_{xyz}. \vis{\beta_{3j}}\!=\!\gamma_{j x y z} \! \Rightarrow\! \Pred_{OT_{x y z}}\!
-     \land\! \alpha_{x y z}\!=\!\tau \land  
-     \Pred_{s_{31},t_{x y z}}\subst{\Post_3\uplus\Post_{OT_{x y z}}}\right)$
+   \!\left( \forall j\in J_{z}. \vis{\beta_{3j}}\!=\!\gamma_{jz} \! \Rightarrow\! \Pred_{OT_{z}}\!
+     \land\! \alpha_{z}\!=\!\tau \land  
+     \Pred_{s_{31},t_{x}}\subst{\Post_3\uplus\Post_{OT_{z}}}\right)$
 
@@
            \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {t \OTWeakarrow {\tau} t_x}
+         {t \OTWeakarrow {\tau} u_x}
 \qquad
@@
          {
-           \gamma_{j x y}^{j\in J_{x y}}, \Pred_{OT_{x y}},\Post_{OT_{x y}}}
-         {t_x \OTWeakarrow {\alpha_{x y}} t_{x y}}
+           \gamma_{j y}^{j\in J_{y}}, \Pred_{OT_{ y}},\Post_{OT_{y}}}
+         {u_x \OTWeakarrow {\alpha_{y}} v_{y}}
 \qquad
@@
          {
-           \gamma_{j x y z}^{j\in J_{x y z}}, \Pred_{OT_{x y z}}, \Post_{OT_{x y z}}}
-         {t_{x y} \OTWeakarrow {\tau} t_{x y z}}
+           \gamma_{jz}^{j\in J_{z}}, \Pred_{OT_{z}}, \Post_{OT_{z}}}
+         {v_{y} \OTWeakarrow {\tau} t_{x}}
 \\ 
-\set{\gamma}=\gamma_{j x}^{j\in J_{x}} \dotcup \gamma_{j x y}^{j\in J_{x y}} \subst{\Post_{OT_x}} \dotcup\gamma_{j x y z}^{j\in J_{x y z}} \subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}\\
+\set{\gamma'}=\gamma_{j x}^{j\in J_{x}} \dotcup \gamma_{j x y}^{j\in J_{x y}} \subst{\Post_{OT_x}} \dotcup\gamma_{j x y z}^{j\in J_{x y z}} \subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}\\
 \Pred=\Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}}\land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}\\
-\Post= \Post_{OT_{x y z}} \shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_{x}}\quad \alpha'_{x y}=\alpha_{x y}\subst{\Post_{OT_x}}\\
+\Post= \Post_{OT_{x y z}} \shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_{x}}\quad \alpha'_{x y}=\alpha_{y}\subst{\Post_{OT_x}}\\
 }
@@
 		\Pred, \Post}  
-         {t \OTWeakarrow {\alpha'_{x y}} t_{x y z}} 
+         {t \OTWeakarrow {\alpha'_{y}} t_{x}} 
 } 
@@
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}}\displaystyle{\bigvee_{z\in Z}}
-   \left( \forall j\in J_{x y z}. \gamma_j=\gamma_{j x y z}  \Rightarrow \Pred_{OT_{x y z}}
-     \land \alpha \!=\! \alpha_{x y}' \land  
-     \Pred_{s',t_{x y z}}\subst{\Post_{OT}\uplus\Post\,}\right)$
+   ( \forall j\in J. \gamma_j'=\gamma_{j}  \Rightarrow \Pred
+     \land \alpha \!=\! \alpha_{y}' \land  
+     \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,})$
+
 Let's start with the hypothesis we have:\\
@@
      \Pred_{s_{11},t_x}\subst{\Post_1\uplus\Post_{OT_x}}\right)$\\
-The conjunction of the term $\Pred_2\subst{\Post_1}$ with the both sides of the implication, we get:\\  
+The conjunction of the predicate $\Pred_2\subst{\Post_1}$ with the both sides of the implication, we get:\\  
 $(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
@@
  \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
-   \!\!\Big(\forall j\in J_x. \vis{\beta_{1j}}\!\!=\!\gamma_{jx}  \Rightarrow \Pred_{OT_x}
-     \!\land\! \alpha_x\!=\!\tau \land\Big(\displaystyle{\bigvee_{y\in Y}}
-    \forall j\in J_{x y}.
-\vis{\beta_{2j}}\!\!=\!\!\gamma_{jx y} \\ \Rightarrow \Pred_{OT_{x y}}\land \alpha\!=\!\alpha_{x y}\!
-\land \Pred_{s_{21},t_{x y}}\subst{\Post_2\uplus\Post_{OT_{x y}}}\Big)\subst{\Post_1\uplus\Post_{OT_x}} \Big)$\\
-Furthermore, the rewriting of the formula  gives \TODO{ajouter argument $\alpha\!=\!\alpha_{x y} \subst{\Post_1\uplus\Post_{OT_x}}$ et $\vis{\beta_{2j}}\subst{\Post_1\uplus\Post_{OT_x}} \!=\!\gamma_{jx y}$}:\\
+   \!\!(\forall j\in J_x. \vis{\beta_{1j}}\!\!=\!\gamma_{jx}  \Rightarrow \Pred_{OT_x}
+     \land \alpha_x\!=\!\tau \land\Big(\displaystyle{\bigvee_{y\in Y}}(
+    \forall j\in J_{y}.
+\vis{\beta_{2j}}\!=\!\gamma_{jy} \\ \Rightarrow \Pred_{OT_{y}}\land \alpha'\!=\!\alpha_{y}\!
+\land \Pred_{s_{21},t_{y}'}\subst{\Post_2\uplus\Post_{OT_{y}}}\Big)\subst{\Post_1\uplus\Post_{OT_x}})$\\
+Furthermore, the rewriting of the formula  gives:\\
 $(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} 
-\Big(\forall j\in J_x.
-\vis{\beta_{1j}}\!\!=\!\!\gamma_{jx} \land  \forall j \in J_{x y}.
-\vis{\beta_{2j}}\subst{\Post_1\uplus\Post_{OT_x}} \!=\!\gamma_{jx y}  \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_1\uplus\Post_{OT_x}} \land \alpha_x\!=\!\tau \land (\alpha\!=\!\alpha_{x y}) \subst{\Post_1\uplus\Post_{OT_x}} \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{x y}}\shortotimes \Post_{OT_x}}\Big)$\\
-As $Post_1$  does not act on $\gamma_{jx y}$, nor on $ \Pred_{OT_{x y}}$ and $  \alpha_{x y}$, the formula can be simplified as follows:\\
+(\forall j\in J_x.
+\vis{\beta_{1j}}\!\!=\!\gamma_{jx} \land  \forall j \in J_{y}.
+(\vis{\beta_{2j}}\!=\!\gamma_{jy})\subst{\Post_1\uplus\Post_{OT_x}}   \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_1\uplus\Post_{OT_x}} \land \alpha_x\!=\!\tau \land (\alpha'\!=\!\alpha_{y}) \subst{\Post_1\uplus\Post_{OT_x}} \land \Pred_{s_{21},t_{y}'}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{y}}\shortotimes \Post_{OT_x}})$\\
+As $Post_1$  does not act on $\gamma_{jy}$, nor on $ \Pred_{OT_{y}}$ and $  \alpha_{y}$, as well $\Post_{OT_x}$  does not act on $\alpha'$, nor on  $\beta_{2j}$ the formula can be simplified as follows:\\
 $(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} 
-\Big(\forall j\in J_x.
-\vis{\beta_{1j}}\!=\!\gamma_{jx} \land  \forall j \in J_{x y}.
-\vis{\beta_{2j}}\subst{\Post_{OT_x}}\!=\!\gamma_{jx y}   \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \subst{\Post_{OT_x}} \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{x y}}\shortotimes \Post_{OT_x}}\Big)$\\
+(\forall j\in J_x.
+\vis{\beta_{1j}}\!=\!\gamma_{jx} \land  \forall j \in J_{y}.
+\vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jy} \subst{\Post_{OT_x}}  \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{y}} \subst{\Post_{OT_x}} \land \alpha_x =\tau \land \alpha'\subst{\Post_1}=\alpha_{y} \subst{\Post_{OT_x}} \land \Pred_{s_{21},t_{y}'}\\\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{y}}\shortotimes \Post_{OT_x}})$\\
 Finally, the conjunction with the term $\Pred_3\subst{\Post_2\shortotimes\Post_1}$ of the both sides of the implication and rewriting, we get:\\
@@
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} 
-\Big(\forall j\in J_x.\vis{\beta^1_j}\!=\!\gamma_{jx} \land  \forall j \in J_{x y}.
-\vis{\beta_{2j}}\subst{\Post_{OT_x}} \!=\!\gamma_{jx y} \Rightarrow \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \alpha_x\!=\!
-\tau \land \alpha\!=\! \alpha_{x y} \subst{\Post_{OT_x}} \land (\Pred_{s_{21},t_{xy}} \land  \Pred_3) \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$\\ 
-Again note that because of the domain independence of the substitution, we removed $\Post_1$ and  we  added  $\Post_{OT_{x y}}\shortotimes\,\Post_{OT_x}$ on the right side of the implication.\\
-Finally, by replacing $(\Pred_{s_{21},t_{xy}} \land  \Pred_3)$
+\Big(\forall j\in J_x.\vis{\beta^1_j}\!=\!\gamma_{jx} \land  \forall j \in J_{y}.
+\vis{\beta_{2j}}\subst{\Post_1}\!=\!\gamma_{jy} \subst{\Post_{OT_x}}\Rightarrow \Pred_{OT_x}\land\Pred_{OT_{y}}\subst{\Post_{OT_x}} \land \alpha_x=\tau \land \alpha'\subst{\Post_1}= \alpha_{y} \subst{\Post_{OT_x}} \land \\(\Pred_{s_{21},t_{y}'} \land  \Pred_3) \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{y}}\shortotimes\Post_{OT_x}})$\\
+Again note that because of the domain independence of the substitution, we removed $\Post_1$ and  we  added the term $\Post_{OT_{y}}\shortotimes\,\Post_{OT_x}$ in the substitution of the right side of the implication.\\
+Finally, by replacing the predicate $(\Pred_{s_{21},t_{y}} \land  \Pred_3)$
 by the conclusion of the  implication given in case 3, we get:\\
 $(\Pred_{s,t} \land \Pred_1)\land \Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\\
-\hspace{1cm} \implies\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} \displaystyle{\bigvee_{z\in Z}} 
-\Big(\forall j\in J_x.\vis{\beta_{1j}}\!=\!\gamma_{jx} \land\!  \forall j \!\in\! J_{x y}.\vis{\beta_{2j}}\subst{\Post_{OT_x}}\!=\!\gamma_{jx y}   \land \\
- \forall j\!\in\! J_{x y z}. \vis{\beta_{3j}} \subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \!=\!\gamma_{j x y z}  \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}} \subst{\Post_{OT_x}} \land \\
-  \Pred_{OT_{x y z}}\!\subst{\Post_{OT_{x y}}\shortotimes\,\Post_{OT_x}} \land \alpha_x\!=\!
-\tau \!\land \alpha\!=\!\alpha_{x y} \subst{\Post_{OT_x}}\land \alpha_{x y z}\!=\!\tau \land \Pred_{s_{31},t_{x y z}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{x y z}}\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}}_{\Post}} \Big)$\\
-Having $s_{31}=s'$ we can conclude:\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} \displaystyle{\bigvee_{z\in Z}} 
+\Big(\forall\! j\in\! J_x.\vis{\beta_{1j}}\!=\!\gamma_{jx} \land  \forall j \!\in\! J_{y}.\vis{\beta_{2j}\subst{\Post_{OT_x}}}\!=\!\gamma_{jy} \subst{\Post_{OT_x}}  \land 
+ \forall j\!\in\!
+J_{z}.
+\vis{\beta_{3j} \subst{\Post_2\,\shortotimes\,\Post_1}} \!=\!\gamma_{jz} \subst{\Post_{OT_{y}}\shortotimes\Post_{OT_x}}  \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{y}} \subst{\Post_{OT_x}} \land\\
+  \Pred_{OT_{z}}\subst{\Post_{OT_{y}}\shortotimes\Post_{OT_x}} \land \alpha_x\!=\!
+\tau \land \alpha'\subst{\Post_1}=\alpha_{y} \subst{\Post_{OT_x}}\land \alpha_{z}\!=\!\tau \land \Pred_{s_{31},t_{z}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{z}}\shortotimes \Post_{OT_{y}}\shortotimes\Post_{OT_x}}_{\Post}} \Big)$\\
+Having $s_{31}=s'$ and $\alpha= \alpha'\subst{\Post_1}$ and rewriting the formula:\\ 
 $\Pred_{s,t} \land \Pred_{OT}\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} \displaystyle{\bigvee_{z\in Z}} 
-\Big(\forall j\in J_{x y z}. \gamma_j =\gamma_{j x y z} \Rightarrow  \Pred \land \alpha =\alpha_{x y}\subst{\Post_{OT_x}} \land \Pred_{s',t_{x y z}}\subst{\Post_{OT}\uplus \Post} \Big)$\\
+(\forall j\in J.
+\vis{\beta_{1j}}\dotcup \vis{\beta_{2j}\subst{\Post_{OT_x}}}\dotcup \vis{\beta_{3j} \subst{\Post_2\,\shortotimes\,\Post_1}}=\\\gamma_{j x} \dotcup \gamma_{jy} \subst{\Post_{OT_x}}  \dotcup \gamma_{jz} \subst{\Post_{OT_{y}}\shortotimes\Post_{OT_x}} \Rightarrow  \Pred \land \alpha_x=
+\tau \land \alpha =\alpha_{y}\subst{\Post_{OT_x}} \land\\ \alpha_{z}=\tau \land \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,}$\\
+we can conclude:\\
  This is exactly what we needed to prove \TODO{je dois generaliser}. \qed

### 2019-05-15 2016-Weak-FH-Bisim/WeakBisim.tex
Proofs

@@
 \end{mathpar}
-we have $(s,t|\Pred_{s,t})\in\mathcal{R}$ by hypothesis and $s=s_{10}$.
-Thus, by  Definition \ref{def-Weak-bisim} we  can deduce there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {u \OTWeakarrow {\alpha_x} u_x}
+by hypothesis we have $(s,t|\Pred_{s,t})\in\mathcal{R}$  and $s=s_{10}$.
+Thus, by  Definition \ref{def-Weak-bisim} we  can deduce there exist weak open transitions $\symb{WOT}_a^{a\in A} \subseteq \WT_2$:
+ \begin{mathpar}
+    \openrule
+         {
+           \gamma_{j a}^{j\in J_{a}}, \Pred_{OT_a},\Post_{OT_a}}
+         {u \OTWeakarrow {\alpha_1} u_a}
 \end{mathpar}
- such that  $\forall x,J_{x}=\{j\in J_1'|\beta_{1j}\neq\tau\}, u=t,  (s_{11},t_x|\Pred_{s_{11},u_x})\in \mathcal{R}$ and \\
+ such that  $\forall a, J_{a}=\{j\in J_1'|\beta_{1j}\neq\tau\}, u=t,  (s_{11},t_a|\Pred_{s_{11},u_a})\in \mathcal{R}$ and \\
  $\Pred_{s,t} \land \Pred_1\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
-  \!\! \left( \forall j\in J_x.\vis{\beta_{1j}}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
-     \land \alpha_x\!=\!\tau \land  
-     \Pred_{s_{11},u_x}\subst{\Post_1\uplus\Post_{OT_x}}\right)$
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
+  \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a}
+     \land \alpha_1\!=\!\tau \land  
+     \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$
 
 Note that, because $\AlgE\cap\AlgA=\emptyset$  (actions and expressions are disjoint) and $\alpha_x\!=\!\tau$ we have 
-directly ($\alpha_x$ cannot be a variable, and cannot contain expressions/variables because $\tau$ has no parameter):
-\begin{mathpar}
-    \openrule
-         {
-           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {u \OTWeakarrow {\tau} u_x}
+directly ($\alpha_a$ cannot be a variable, and cannot contain expressions/variables because $\tau$ has no parameter):
+\begin{mathpar}
+    \openrule
+         {
+           \gamma_{j a}^{j\in J_{a}}, \Pred_{OT_a},\Post_{OT_a}}
+         {u \OTWeakarrow {\tau} u_a}
 \end{mathpar}
+and//
+$\Pred_{s,t} \land \Pred_1\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
+  \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a}
+     \land    \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$
+
 \item Concerning the middle open transition in $\mathcal{T}_1$:
@@
            \beta_{2j}^{j \in J_2'},\Pred_2,\Post_2 }
-         {s_{20} \OTarrow {\alpha} s_{21}} 
+         {s_{20} \OTarrow {\alpha'} s_{21}} 
 \end{mathpar}
-we have  $(s_{11},u_x|\Pred_{s_{11},u_x})\in \mathcal{R}$  and $s_{11}=s_{20}$. Again 
- by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{y}^{y\in Y} \subseteq \WT_2$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{y}^{j\in J_{y}}, \Pred_{OT_{y}},\Post_{OT_{y}}}
-         {u_x \OTWeakarrow {\alpha_{y}} v_{y}}
+we have  $(s_{11},u_a|\Pred_{s_{11},u_a})\in \mathcal{R}$  and $s_{11}=s_{20}$. Again 
+ by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{b}^{b\in B} \subseteq \WT_2$:
+ \begin{mathpar}
+    \openrule
+         {
+           \gamma_{b}^{j\in J_{b}}, \Pred_{OT_{b}},\Post_{OT_{b}}}
+         {u_a \OTWeakarrow {\alpha_{2}} v_{b}}
 \end{mathpar}
- such that  $\forall y, J_{y}=\{j\in J_2'|\beta_{2j}\neq\tau\}, 
+ such that  $\forall b, J_{b}=\{j\in J_2'|\beta_{2j}\neq\tau\}, 
 (s_{21},v_{y}|\Pred_{s_{21},v_{y}})\in \mathcal{R}$; \\
- $\Pred_{s_{11},u_x} \land \Pred_2\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}}
- \!\!  \left( \forall j\in J_{y}. \vis{\beta_{2j}}\!=\!\gamma_{jy}\Rightarrow \Pred_{OT_{y}}\!\land \alpha\!=\!\alpha_{y} \land  
-     \Pred_{s_{21},v_{y}}\subst{\Post_2\uplus\Post_{OT_{y}}}\right)$
+ $\Pred_{s_{11},u_a} \land \Pred_2\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{b\in B}}
+ \!\!  \left( \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}\Rightarrow \Pred_{OT_{b}}\!\land \alpha'\!=\!\alpha_{2} \land  
+     \Pred_{s_{21},v_{b}}\subst{\Post_2\uplus\Post_{OT_{b}}}\right)$
 
@@
 \end{mathpar}
-From previous case, we have $(s_{21},v_{y}|\Pred_{s_{21},v_{y}})\in \mathcal{R}$, and we have $s_{21}=s_{30}$. Then, by
- Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{x}^{z\in Z} \subseteq \WT_2$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{jz}^{j\in J_{z}}, \Pred_{OT_{z}},\Post_{OT_{z}}}
-         {v_{y} \OTWeakarrow {\tau} w_{z}}
+From previous case, we have $(s_{21},v_{b}|\Pred_{s_{21},v_{b}})\in \mathcal{R}$, and we have $s_{21}=s_{30}$. Then, by
+ Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{a}^{c\in C} \subseteq \WT_2$:
+ \begin{mathpar}
+    \openrule
+         {
+           \gamma_{jc}^{j\in J_{c}}, \Pred_{OT_{c}},\Post_{OT_{c}}}
+         {v_{b} \OTWeakarrow {\tau} w_{c}}
 \end{mathpar}
- such that  $\forall z, J_{z}= \{j\in J_3'|\beta_{3j}\neq\tau\}, 
-(s_{31},w_{z}|\Pred_{s_{31},w_{z}})\in \mathcal{R}$,  $w_z=t_x$ and \\
- $\Pred_{s_{21},v_{y}} \land \Pred_3\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{z\in Z}}
-   \!\left( \forall j\in J_{z}. \vis{\beta_{3j}}\!=\!\gamma_{jz} \! \Rightarrow\! \Pred_{OT_{z}}\!
-     \land\! \alpha_{z}\!=\!\tau \land  
-     \Pred_{s_{31},t_{x}}\subst{\Post_3\uplus\Post_{OT_{z}}}\right)$
+ such that  $\forall c, J_{c}= \{j\in J_3'|\beta_{3j}\neq\tau\}, 
+(s_{31},w_{c}|\Pred_{s_{31},w_{c}})\in \mathcal{R}$ and \\
+ $\Pred_{s_{21},v_{b}} \land \Pred_3\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{c\in C}}
+   \!\left( \forall j\in J_{c}. \vis{\beta_{3j}}\!=\!\gamma_{jc} \! \Rightarrow\! \Pred_{OT_{c}}\!
+     \land\!  
+     \Pred_{s_{31},w_{c}}\subst{\Post_3\uplus\Post_{OT_{c}}}\right)$
 
@@
          {
-           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {t \OTWeakarrow {\tau} u_x}
+           \gamma_{j a}^{j\in J_{a}}, \Pred_{OT_x},\Post_{OT_a}}
+         {t \OTWeakarrow {\tau} u_a}
 \qquad
@@
          {
-           \gamma_{j y}^{j\in J_{y}}, \Pred_{OT_{ y}},\Post_{OT_{y}}}
-         {u_x \OTWeakarrow {\alpha_{y}} v_{y}}
+           \gamma_{j b}^{j\in J_{b}}, \Pred_{OT_{ y}},\Post_{OT_{b}}}
+         {u_a \OTWeakarrow {\alpha_2} v_{b}}
 \qquad
@@
          {
-           \gamma_{jz}^{j\in J_{z}}, \Pred_{OT_{z}}, \Post_{OT_{z}}}
-         {v_{y} \OTWeakarrow {\tau} t_{x}}
+           \gamma_{jc}^{j\in J_{c}}, \Pred_{OT_{c}}, \Post_{OT_{c}}}
+         {v_{b} \OTWeakarrow {\tau} w_{c}}
 \\ 
-\set{\gamma'}=\gamma_{j x}^{j\in J_{x}} \dotcup \gamma_{j x y}^{j\in J_{x y}} \subst{\Post_{OT_x}} \dotcup\gamma_{j x y z}^{j\in J_{x y z}} \subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}\\
-\Pred=\Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}}\land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}}\\
-\Post= \Post_{OT_{x y z}} \shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_{x}}\quad \alpha'_{x y}=\alpha_{y}\subst{\Post_{OT_x}}\\
+\set{\gamma'}=\gamma_{j a}^{j\in J_{a}} \dotcup \gamma_{j a b}^{j\in J_{b}} \subst{\Post_{OT_a}} \dotcup\gamma_{jc}^{j\in J_{c}} \subst{\Post_{OT_{ b}}\shortotimes\Post_{OT_a}}\\
+\Pred=\Pred_{OT_a}\land\Pred_{OT_{b}}\subst{\Post_{OT_a}}\land \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}\\
+\Post= \Post_{OT_{c}} \shortotimes \Post_{OT_{b}}\shortotimes\Post_{OT_{a}}\quad \alpha''=\alpha_{2}\subst{\Post_{OT_a}}\\
 }
@@
 		\Pred, \Post}  
-         {t \OTWeakarrow {\alpha'_{y}} t_{x}} 
+         {u \OTWeakarrow {\alpha''} w_{c}} 
 } 
  \end{mathpar}
-So we need to prove that the following statement holds:\\
+So need to prove that the following statement holds:\\
 $\Pred_{s,t} \land \Pred\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}}\displaystyle{\bigvee_{z\in Z}}
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} 
   ( \forall j\in J. \gamma_j'=\gamma_{j}  \Rightarrow \Pred
-     \land \alpha \!=\! \alpha_{y}' \land  
-     \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,})$
-
-Let's start with the hypothesis we have:\\
+     \land \alpha \!=\! \alpha'' \land  
+     \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,})$\\
+     Let's start with the hypothesis and consider  $u=t$   we have:\\
 $\Pred_{OT}= \Pred_1 \wedge \Pred_2\subst{\Post_1} \wedge \Pred_3\subst{\Post_2\shortotimes\Post_1}$\\
@@
 $\Pred_{s,t} \land \Pred_1\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
- \! \! \left( \forall j\in J_x. \vis{\beta_{1j}}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
-     \land \alpha_x\!=\!\tau \land  
-     \Pred_{s_{11},t_x}\subst{\Post_1\uplus\Post_{OT_x}}\right)$\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
+ \! \! \left( \forall j\in J_a. \vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a}
+      \land  
+     \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$\\
 The conjunction of the predicate $\Pred_2\subst{\Post_1}$ with the both sides of the implication, we get:\\  
 $(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
- \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
-  \!\! \left( \forall j\in J_x. \vis{\beta_{1j}}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
-     \land \alpha_x\!=\!\tau \land  
-     \Pred_{s_{11},t_x}\subst{\Post_1\uplus\Post_{OT_x}}\right) \wedge\Pred_2\subst{\Post_1\uplus\Post_{OT_x}}  \\
+ \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
+  \!\! ( \forall j\in J_a. \vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a} \land
+     \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}) \wedge\\ \Pred_2\subst{\Post_1\uplus\Post_{OT_a}}  \\
 $
@@
 $(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
- \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
-\!\!   \left(\forall j\in J_x. \vis{\beta_{1j}}\!=\!\gamma_{jx}\Rightarrow \Pred_{OT_x}
-     \!\land\! \alpha_x\!=\!\tau\land(\Pred_{s_{11},t_x}\wedge\Pred_2)\subst{\Post_1\uplus\Post_{OT_x}} \right)$\\
-By replacing the inner sub-term $(\Pred_{s_{11},t_x}\wedge\Pred_2)$ by the conclusion of the  implication given in case 2,  the formula becomes: \\
+ \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
+\!\!   \left(\forall j\in J_a. \vis{\beta_{1j}}\!=\!\gamma_{ja}\Rightarrow \Pred_{OT_a}
+     \!\land(\Pred_{s_{11},u_a}\wedge\Pred_2)\subst{\Post_1\uplus\Post_{OT_a}} \right)$\\
+By replacing the inner predicate $(\Pred_{s_{11},u_a}\wedge\Pred_2)$ by the conclusion of the  statement given in case 2,  the formula becomes: \\
 $(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
- \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
-   \!\!(\forall j\in J_x. \vis{\beta_{1j}}\!\!=\!\gamma_{jx}  \Rightarrow \Pred_{OT_x}
-     \land \alpha_x\!=\!\tau \land\Big(\displaystyle{\bigvee_{y\in Y}}(
-    \forall j\in J_{y}.
-\vis{\beta_{2j}}\!=\!\gamma_{jy} \\ \Rightarrow \Pred_{OT_{y}}\land \alpha'\!=\!\alpha_{y}\!
-\land \Pred_{s_{21},t_{y}'}\subst{\Post_2\uplus\Post_{OT_{y}}}\Big)\subst{\Post_1\uplus\Post_{OT_x}})$\\
+ \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
+   \!\!(\forall j\in J_a. \vis{\beta_{1j}}\!\!=\!\gamma_{ja}  \Rightarrow \Pred_{OT_a}
+      \land (\displaystyle{\bigvee_{b\in B}}(
+    \forall j\in J_{b}.
+\vis{\beta_{2j}}\!=\!\gamma_{jb}  \Rightarrow \Pred_{OT_{b}}\land \alpha'\!=\!\alpha_2\!
+\land \Pred_{s_{21},v_{b}}\subst{\Post_2\uplus\Post_{OT_{b}}})\subst{\Post_1\uplus\Post_{OT_a}})$\\
 Furthermore, the rewriting of the formula gives:\\
 $(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} 
-(\forall j\in J_x.
-\vis{\beta_{1j}}\!\!=\!\gamma_{jx} \land  \forall j \in J_{y}.
-(\vis{\beta_{2j}}\!=\!\gamma_{jy})\subst{\Post_1\uplus\Post_{OT_x}}   \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_1\uplus\Post_{OT_x}} \land \alpha_x\!=\!\tau \land (\alpha'\!=\!\alpha_{y}) \subst{\Post_1\uplus\Post_{OT_x}} \land \Pred_{s_{21},t_{y}'}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{y}}\shortotimes \Post_{OT_x}})$\\
-As $Post_1$  does not act on $\gamma_{jy}$, nor on $ \Pred_{OT_{y}}$ and $  \alpha_{y}$, as well $\Post_{OT_x}$  does not act on $\alpha'$, nor on  $\beta_{2j}$ the formula can be simplified as follows:\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}} 
+(\forall j\in J_a.
+\vis{\beta_{1j}}\!\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
+(\vis{\beta_{2j}}\!=\!\gamma_{jb})\subst{\Post_1\uplus\Post_{OT_a}}   \Rightarrow\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_1\uplus\Post_{OT_a}} \land  (\alpha'\!=\!\alpha_{2}) \subst{\Post_1\uplus\Post_{OT_a}} \land \\ \Pred_{s_{21},v_{b}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
+Since $Post_1$  does not act on $\gamma_{jb}$, nor on $ \Pred_{OT_{b}}$ and $  \alpha_{2}$, as well $\Post_{OT_a}$  does not act on $\alpha'$, nor on  $\beta_{2j}$ the formula can be simplified as follows:\\
 $(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} 
-(\forall j\in J_x.
-\vis{\beta_{1j}}\!=\!\gamma_{jx} \land  \forall j \in J_{y}.
-\vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jy} \subst{\Post_{OT_x}}  \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{y}} \subst{\Post_{OT_x}} \land \alpha_x =\tau \land \alpha'\subst{\Post_1}=\alpha_{y} \subst{\Post_{OT_x}} \land \Pred_{s_{21},t_{y}'}\\\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{y}}\shortotimes \Post_{OT_x}})$\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}} 
+(\forall j\in J_a.
+\vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
+\vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jb} \subst{\Post_{OT_a}}  \Rightarrow\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_{OT_a}} \land \alpha'\subst{\Post_1}=\alpha_{2} \subst{\Post_{OT_a}} \land \Pred_{s_{21},v_b}\\\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
 Finally, the conjunction with the term $\Pred_3\subst{\Post_2\shortotimes\Post_1}$ of the both sides of the implication and rewriting, we get:\\
@@
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} 
-\Big(\forall j\in J_x.\vis{\beta^1_j}\!=\!\gamma_{jx} \land  \forall j \in J_{y}.
-\vis{\beta_{2j}}\subst{\Post_1}\!=\!\gamma_{jy} \subst{\Post_{OT_x}}\Rightarrow \Pred_{OT_x}\land\Pred_{OT_{y}}\subst{\Post_{OT_x}} \land \alpha_x=\tau \land \alpha'\subst{\Post_1}= \alpha_{y} \subst{\Post_{OT_x}} \land \\(\Pred_{s_{21},t_{y}'} \land  \Pred_3) \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{y}}\shortotimes\Post_{OT_x}})$\\
-Again note that because of the domain independence of the substitution, we removed $\Post_1$ and  we  added the term $\Post_{OT_{y}}\shortotimes\,\Post_{OT_x}$ in the substitution of the right side of the implication.\\
-Finally, by replacing the predicate $(\Pred_{s_{21},t_{y}} \land  \Pred_3)$
+(\forall j\in J_a.\vis{\beta^1_j}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
+\vis{\beta_{2j}}\subst{\Post_1}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}\Rightarrow \Pred_{OT_a}\land\Pred_{OT_{b}}\subst{\Post_{OT_a}} \land  \alpha'\subst{\Post_1}= \alpha_{2} \subst{\Post_{OT_a}} \land (\Pred_{s_{21},v_b} \land  \Pred_3)\\ \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{b}}\shortotimes\Post_{OT_a}})$\\
+Again note that because of the domain independence of the substitution, we removed $\Post_1$ and  we  added the term $\Post_{OT_{b}}\shortotimes\,\Post_{OT_a}$ in the substitution of the right side of the implication.\\
+Finally, by replacing the predicate $(\Pred_{s_{21},v_{b}} \land  \Pred_3)$
 by the conclusion of the  implication given in case 3, we get:\\
-$(\Pred_{s,t} \land \Pred_1)\land \Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} \displaystyle{\bigvee_{z\in Z}} 
-\Big(\forall\! j\in\! J_x.\vis{\beta_{1j}}\!=\!\gamma_{jx} \land  \forall j \!\in\! J_{y}.\vis{\beta_{2j}\subst{\Post_{OT_x}}}\!=\!\gamma_{jy} \subst{\Post_{OT_x}}  \land 
- \forall j\!\in\!
-J_{z}.
-\vis{\beta_{3j} \subst{\Post_2\,\shortotimes\,\Post_1}} \!=\!\gamma_{jz} \subst{\Post_{OT_{y}}\shortotimes\Post_{OT_x}}  \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{y}} \subst{\Post_{OT_x}} \land\\
-  \Pred_{OT_{z}}\subst{\Post_{OT_{y}}\shortotimes\Post_{OT_x}} \land \alpha_x\!=\!
-\tau \land \alpha'\subst{\Post_1}=\alpha_{y} \subst{\Post_{OT_x}}\land \alpha_{z}\!=\!\tau \land \Pred_{s_{31},t_{z}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{z}}\shortotimes \Post_{OT_{y}}\shortotimes\Post_{OT_x}}_{\Post}} \Big)$\\
-Having $s_{31}=s'$ and $\alpha= \alpha'\subst{\Post_1}$ and rewriting the formula:\\ 
+$\Pred_{s,t} \land \underbrace{\Pred_1\land \Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}}_{\Pred_{OT}}\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}}\, \displaystyle{\bigvee_{c\in C}} 
+(\forall\! j\in\! J_a.\vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \!\in\! J_{b}.\vis{\beta_{2j}\subst{\Post_{OT_a}}}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}  \land 
+ \forall j\!\in\! J_{c}. \vis{\beta_{3j} \subst{\Post_2\,\shortotimes\,\Post_1}} \!=\!\gamma_{jc} \subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}  \Rightarrow\\
+   \underbrace{\Pred_{OT_a}\land\Pred_{OT_{b}} \subst{\Post_{OT_a}} \land 
+  \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}}_{\Pred} \land  \underbrace{\alpha'\subst{\Post_1}}_{\alpha}=\underbrace{\alpha_{2} \subst{\Post_{OT_a}}}_{\alpha''} \land\\ \Pred_{s_{31},w_{c}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{c}}\shortotimes \Post_{OT_{b}}\shortotimes\Post_{OT_a}}_{\Post}})$\\
+ \TODO{Comment passer a ca?}\\
+$\forall j\in J_a\uplus J_b\uplus J_c.
+\vis{\beta_{1j}}\dotcup \vis{\beta_{2j}\subst{\Post_{OT_a}}}\dotcup \vis{\beta_{3j} \subst{\Post_2\,\shortotimes\,\Post_1}}=\gamma_{j a} \dotcup \gamma_{jb} \subst{\Post_{OT_a}}  \dotcup \gamma_{jc} \subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}
+$ \\
+We have  $s_{31}=s'$, so can rewrite the formula:\\
 $\Pred_{s,t} \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} \displaystyle{\bigvee_{z\in Z}} 
-(\forall j\in J.
-\vis{\beta_{1j}}\dotcup \vis{\beta_{2j}\subst{\Post_{OT_x}}}\dotcup \vis{\beta_{3j} \subst{\Post_2\,\shortotimes\,\Post_1}}=\\\gamma_{j x} \dotcup \gamma_{jy} \subst{\Post_{OT_x}}  \dotcup \gamma_{jz} \subst{\Post_{OT_{y}}\shortotimes\Post_{OT_x}} \Rightarrow  \Pred \land \alpha_x=
-\tau \land \alpha =\alpha_{y}\subst{\Post_{OT_x}} \land\\ \alpha_{z}=\tau \land \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,}$\\
-we can conclude:\\
- This is exactly what we needed to prove \TODO{je dois generaliser}. \qed
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}} \displaystyle{\bigvee_{b\in B}} \displaystyle{\bigvee_{c\in C}} 
+(\forall j\in J.\gamma_j'=\gamma_j \Rightarrow  \Pred \land \alpha=\alpha''  \land \Pred_{s',w_{c}}\subst{\Post_{OT}\uplus\Post\,}$\\
+Thus, we can conclude: \TODO{que dire pour passer ici}\\
+$\Pred_{s,t} \land \Pred_{OT}\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} 
+(\forall j\in J.\gamma_j'=\gamma_j \Rightarrow  \Pred \land \alpha=\alpha''  \land \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,}$\\
+ This is exactly what we needed to prove. \qed
 \end{proof}
@@
 \newpage
-\begin{proof} Suppose we have: 
+\begin{proof} Suppose that we have: 
 \begin{mathpar}
@@
 \set{\gamma}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!
-\Post_{1j}}}\dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }}
+\Post_{1j}}}\dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }}
 \\
@@
 $s_l=s_{0l} \wedge s_{(m_1+1)l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)l}=s'_l$
-$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\}$,\\
+and $\forall j\in (J\setminus \Holes(Q))\cup \{j_0\}$,\\
 $\set{\gamma}_j=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1ij}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}}\dotcup  \vis{\set{\beta_{2j}}\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}} \dotcup\\
@@
 				}%\]
-$ 
+$\\ 
 In this equation, and using cases 1, 2 and 3 above, we have for all $k\in [0\ldots n_1+n_2+2]$, $\beta_{kj_0}=\alpha_k$.
@@
 			{
-				(\beta_{1pj})^{j\in J\cap\Holes(Q)}, {{\Pred''{1p}}},  
+				(\beta_{1pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_{1p}}},  
 				{{\Post''_{1p}}}}
@@
 				{{\Post''_2}}}
-				{\ostate{v_{n_k'l}^{l\in L_Q}} \OTarrow {\alpha_k}
-				\ostate{v_{(n_k'+1)l}^{l\in L_Q}}}
+				{\ostate{v_{n_kl}^{l\in L_Q}} \OTarrow {\alpha_k}
+				\ostate{v_{(n_k+1)l}^{l\in L_Q}}}
 				}%\]
@@
 			{
-			(\gamma_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred^b_k}},  
-				{{\Post^b_k}}}
+			(\gamma_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
+				{{\Post_k}}}
 			{\ostate{v_{l}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
@@
 ~~\qquad \mybigdotcup_{i=n_k+1}^{n_k'-1}
-\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=n_k-1}^{0}\!\!\!\Post''_{1j}} }\\
+\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\!\!\bigotimes_{j=n_k-1}^{0}\!\!\!\Post''_{1j}} }\\
 \Pred_k=\bigwedge_{i=0}^{n_k-1}\!\!\Pred''_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred''_2 \subst{\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{1j}}\land\\ 
-~\qquad\quad\bigwedge_{i=n_k+1}^{n_k'-1}\!\!\!\Pred''_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=n_k-1}^{0}\!\!\!\Post''_{1j}}\\
-\Post_k= \bigotimes_{j=n_k'-1}^{0}\!\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{1j}$\\
+~\qquad\quad\bigwedge_{i=n_k+1}^{n_k'-1}\!\!\!\Pred''_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\!\!\bigotimes_{j=n_k-1}^{0}\!\!\!\Post''_{1j}}\\
+\Post_k= \bigotimes_{j=n_k'-1}^{0}\!\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\!\!\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{1j}$\\
 
@@
 \alpha'_n]$ is a a list of $\alpha_p$ such that $p\in [0..(n_1\!+\!n_2\!+\!2)] \land \alpha_p\neq \tau$ where for all $k\in [0\ldots n_1+n_2+2]$, $\beta_{kj_0}=\alpha_k$.
-In other words, $\displaystyle{\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{i{j_0}}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{i{j_0}}} = [\alpha'_0..
+In other words, $\displaystyle{\mybigdotcup_{i=0}^{m_1}  \vis{\beta_{1i{j_0}}} \dotcup  \vis{\set{\beta_{2i}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3i{j_0}}} = [\alpha'_0..
 \alpha'_n]}$.
@@
 			\gamma_{kj}^{j\in J_k}, {\Pred_k}, {\Post_k}}
-			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha_{k}}
+			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
 				\ostate{s_{(p+1)l}^{l\in L_Q}}}
@@
 \end{mathpar}
-and $\displaystyle{\bigcup_{p=0}^nJ_{p}} = J\cap\Holes(Q)$, $\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}}$, $\forall l\in L_Q,\, s_{0l}=s_l$, $s_{(n+1)l}=s'_l$  \\
-  $\Pred = \Pred\,'
-		\land \displaystyle{\bigwedge_{p=0}^n}((\alpha_p= \beta_{pj_0}\land \Pred_p)\bigotimes_{i=p-1}^{0}\Post_i),\text{and~}$\\
-$\displaystyle{\Post=\Post\,'\uplus\bigotimes_{p=n}^0
-		\Post_p}$  \\
-We have:\\
-$\Pred=\displaystyle{\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\land 
-\bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}}$\\
-By replacing $\Pred_{1i}$,  $\Pred_2$, and $\Pred_{3i}$ by their equivalent formula  we obtain:\\
+We have by 	hypothesis: 	$s_{0l}=s_l$, $s_{(n+1)l}=s'_l$\\
+By considering $n=m_1+m_2+2$,  and $\forall p \in [0..n]$: \\
+$\Pred_{p}= \left\{
+ \begin{array}{ll}
+\Pred_{1p} & \mbox{if }p<m_1\\
+\Pred_{2} & \mbox{if } p=m_1\\
+\Pred_{1(p-m_1)} & \mbox{if }p\geq m_1\\
+\end{array}
+\right. 
+\quad$
+ $\qquad
+\Post_{p}= \left\{
+ \begin{array}{ll}
+\Post_{1p} & \mbox{if }p<m_1\\
+\Post_{2} & \mbox{if } p=m_1\\
+\Post_{1(p-m_1)} & \mbox{if }p\geq m_1\\
+\end{array}
+\right. 
+$\\
+and similarly for $\beta_p$. Thus, we can rewrite $\gamma$ given in the hypothesis as: \\
+$\set{\gamma}= \displaystyle{\mybigdotcup_{p=0}^{n}
+\vis{\set{\beta_{p}}}\subst{\bigotimes_{p=n}^{0} \Post_{p}}}$\\
+Furthermore, still by hypothesis we have:\\
+$\Pred=\displaystyle{\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }\land \\
+~\qquad \quad \bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}$\\
+By replacing $\Pred_{1i}$,  $\Pred_2$, and $\Pred_{3i}$ by their equivalent formula obtained from cases 1, 2 and 3 we have:\\
 $\Pred =\displaystyle{\bigwedge_{i=0}^{m_1}({\Pred'_{1i}}
 		\land {\Pred''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}) \bigotimes_{j=i-1}^{0}\subst{\Post_{1j}}\land}\\
-~~\qquad\qquad\qquad({\Pred'_2}\land {\Pred''_2}\land \alpha_2=\beta_{2j_0})	\bigotimes_{i=m_1}^{0}\subst{\Post_{1i}}\land\\
+~~\qquad\qquad({\Pred'_2}\land {\Pred''_2}\land \alpha_2=\beta_{2j_0})	\bigotimes_{i=m_1}^{0}\subst{\Post_{1i}}\land\\
 ~~\qquad\qquad\bigwedge_{i=0}^{m_2} ({\Pred'_{3i}}\land {\Pred''_{3i}}\land \alpha_{3i}=\beta_{3ij_0})
 \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}$\\
-By distribution of the substitution operation over the logical operator we can deduce:\\
+By distribution of the substitution operation over the logical operator we reformulate as:\\
 $\Pred= \displaystyle{\big(\bigwedge_{i=0}^{m_1}
@@
 \land{\Pred'_2}\bigotimes_{i=m_1}^{0}\subst{{\Post'_{1i}}}\land} \\
-~~\qquad\qquad\quad\big(\bigwedge_{i=0}^{m_2}{\Pred'_{3i}}\bigotimes_{j=i-1}^{0}\subst{{\Post'_{3j}}}\subst{{\Post'_2}}\bigotimes_{j=m_1}^{0}\subst{{\Post'_{1j}}}\big) \land\\	
-~\qquad\qquad\quad\bigwedge_{i=0}^{m_1}({\Pred''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}) \bigotimes_{j=i-1}^{0}\subst{\Post_{1j}}\land({\Pred''_2}\land \alpha_2=\beta_{2j_0})	\bigotimes_{i=m_1}^{0}\subst{\Post_{1i}}\land\\
-~\qquad\qquad\quad\bigwedge_{i=0}^{m_2} ({\Pred''_{3i}}\land \alpha_{3i}=\beta_{3ij_0})\bigotimes_{j=i-1}^{0}\subst{\Post_{3j}}\subst{\Post_2}  \bigotimes_{i=m_1}^{0}\subst{\Post_{1i}}
+~~\qquad\qquad\bigwedge_{i=0}^{m_2}{\Pred'_{3i}}\bigotimes_{j=i-1}^{0}\subst{{\Post'_{3j}}}\subst{{\Post'_2}}\bigotimes_{j=m_1}^{0}\subst{{\Post'_{1j}}} \land\\	
+~\qquad\qquad\bigwedge_{i=0}^{m_1}({\Pred''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}) \bigotimes_{j=i-1}^{0}\subst{\Post_{1j}}\land({\Pred''_2}\land \alpha_2=\beta_{2j_0})	\bigotimes_{i=m_1}^{0}\subst{\Post_{1i}}\land\\
+~\qquad\qquad\bigwedge_{i=0}^{m_2} ({\Pred''_{3i}}\land \alpha_{3i}=\beta_{3ij_0})\bigotimes_{j=i-1}^{0}\subst{\Post_{3j}}\subst{\Post_2}  \bigotimes_{i=m_1}^{0}\subst{\Post_{1i}}
 $\\		
-Therefore, we have:\\
-$\Pred= \Pred\,' \wedge \displaystyle{\bigwedge_{p=0}^{n}}((\alpha_p= \beta_{pj_0}\land \Pred_p)\bigotimes_{i=p-1}^{0}\Post_i)$\\ where $n=m_1+m_2+1$	\\
-Concerning the postcondition we have:\\
+Thus, we can write the formula as follows:\\
+$\Pred= \Pred\,' \wedge \displaystyle{\bigwedge_{p=0}^{n}}((\alpha_p= \beta_{pj_0}\land \Pred_p)\bigotimes_{i=p-1}^{0}\Post_i)$\\
+We proceed the same way with the postcondition,  we have:\\
 $\Post=\displaystyle{\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}$\\
-By replacing ${\Post_{1i}}$,  $\Post_2$, and ${\Post_{3i}}$ and because the ${\Post'_i}$ and ${\Post''_i}$ are independent (the ${\Post'_i}$ concern the leaves of $P$ while the ${\Post''_i}$ concern the leaves of $Q$), we obtain:\\
+By replacing ${\Post_{1i}}$,  $\Post_2$, and ${\Post_{3i}}$ their values obtained from the cases 1, 2, and 3, and because the ${\Post'_i}$ and ${\Post''_i}$ are independent (the ${\Post'_i}$ concern the leaves of $P$ while the ${\Post''_i}$ concern the leaves of $Q$), we obtain:\\
 $\Post= \displaystyle{\bigotimes_{i=m_2}^{0}\subst{{\Post'_{3i}}\uplus 
@@
 ~~\qquad= \Post' \uplus \bigotimes_{j=n}^{0} \Post_j $\\
- where $n=m_1+m_2+1$	
+\qed
 \end{proof}

### 2019-06-26 2016-Weak-FH-Bisim/WeakBisim.tex
corrections d indice et d anglais en page 43-44

@@
 \begin{proof} 
-($\Rightarrow$) Firstly, we prove that Definition \ref{def-Weak-bisim} implies definition above.\\
+($\Rightarrow$) First, we prove that Definition \ref{def-Weak-bisim} implies the definition above. In other words,
 Suppose that $\Pred_{s,t}\in \mathcal{R}$ 
@@
 
-For the sake of simplicity, we prove the rule in the  restricted case where $n$ and $m$ to be equal to $1$, hence a single tau open transition will be considered on each side of the potentially visible one.
+For the sake of simplicity, we prove the rule in the  restricted case where $n$ and $m$ are equal to $1$, hence a single tau open transition will be considered on each side of the potentially visible one.
 The proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule.
@@
            \gamma_{j a}^{j\in J_{a}}, \Pred_{OT_a},\Post_{OT_a}}
-         {u \OTWeakarrow {\alpha_1} u_a}
+         {u \OTWeakarrow {\alpha_{1 a}} u_a}
 \end{mathpar}
- such that  $\forall a, J_{a}=\{j\in J_1'|\beta_{1j}\neq\tau\}, u=t,  (s_{11},t_a|\Pred_{s_{11},u_a})\in \mathcal{R}$ and \\
+ such that  $\forall a, J_{a}=\{j\in J_1'|\beta_{1j}\neq\tau\}, u=t,  (s_{11},u_a|\Pred_{s_{11},u_a})\in \mathcal{R}$ and \\
  $\Pred_{s,t} \land \Pred_1\\
@@
   \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a}
-     \land \alpha_1\!=\!\tau \land  
+     \land \alpha_{1 a}\!=\!\tau \land  
      \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$
 
-Note that, because $\AlgE\cap\AlgA=\emptyset$  (actions and expressions are disjoint) and $\alpha_x\!=\!\tau$ we have 
-directly ($\alpha_a$ cannot be a variable, and cannot contain expressions/variables because $\tau$ has no parameter):
+ Note that, because $\AlgE\cap\AlgA=\emptyset$  (actions and expressions are disjoint) and $\alpha_{1 a}\!=\!\tau$ we have 
+directly ($\alpha_{1 a}$ cannot be a variable, and cannot contain expressions/variables because $\tau$ has no parameter):
 \begin{mathpar}
@@
 \end{mathpar}
-and//
-$\Pred_{s,t} \land \Pred_1\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
-  \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a}
-     \land    \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$
+%and\\
+%$\Pred_{s,t} \land \Pred_1\\
+%\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
+%  \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a}
+%     \land    \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$
+%
 
@@
          {
-           \gamma_{b}^{j\in J_{b}}, \Pred_{OT_{b}},\Post_{OT_{b}}}
-         {u_a \OTWeakarrow {\alpha_{2}} v_{b}}
+           \gamma_{j b}^{j\in J_{b}}, \Pred_{OT_{b}},\Post_{OT_{b}}}
+         {u_a \OTWeakarrow {\alpha_{2 b}} v_{b}}
 \end{mathpar}
  such that  $\forall b, J_{b}=\{j\in J_2'|\beta_{2j}\neq\tau\}, 
-(s_{21},v_{y}|\Pred_{s_{21},v_{y}})\in \mathcal{R}$; \\
+(s_{21},v_{b}|\Pred_{s_{21},v_{b}})\in \mathcal{R}$; \\
  $\Pred_{s_{11},u_a} \land \Pred_2\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{b\in B}}
- \!\!  \left( \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}\Rightarrow \Pred_{OT_{b}}\!\land \alpha'\!=\!\alpha_{2} \land  
+ \!\!  \left( \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}\Rightarrow \Pred_{OT_{b}}\!\land \alpha'\!=\!\alpha_{2 b} \land  
      \Pred_{s_{21},v_{b}}\subst{\Post_2\uplus\Post_{OT_{b}}}\right)$
 
-\item Similarly to the case 1,  the third  open transition in $\mathcal{T}_1$:
+\item Similarly to the case 1, we consider the third  open transition in $\mathcal{T}_1$:
      \begin{mathpar}
@@
 \\ 
-\set{\gamma'}=\gamma_{j a}^{j\in J_{a}} \dotcup \gamma_{j a b}^{j\in J_{b}} \subst{\Post_{OT_a}} \dotcup\gamma_{jc}^{j\in J_{c}} \subst{\Post_{OT_{ b}}\shortotimes\Post_{OT_a}}\\
+\set{\gamma'}=\gamma_{j a}^{j\in J_{a}} \dotcup \gamma_{j b}^{j\in J_{b}} \subst{\Post_{OT_a}} \dotcup\gamma_{jc}^{j\in J_{c}} \subst{\Post_{OT_{ b}}\shortotimes\Post_{OT_a}}\\
 \Pred=\Pred_{OT_a}\land\Pred_{OT_{b}}\subst{\Post_{OT_a}}\land \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}\\
@@
  \end{mathpar}
-So need to prove that the following statement holds:\\
+We now need to prove that the following statement holds:\\
 $\Pred_{s,t} \land \Pred\\
@@
      \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,})$\\
-     Let's start with the hypothesis and consider  $u=t$   we have:\\
+     Let's start with the hypothesis \TODO{ je vois pas ce que u=t apporte -- Ludo} and consider  $u=t$   we have:\\
 $\Pred_{OT}= \Pred_1 \wedge \Pred_2\subst{\Post_1} \wedge \Pred_3\subst{\Post_2\shortotimes\Post_1}$\\
 $\Post_{OT}=\Post_3\shortotimes \Post_2\shortotimes\Post_1$\\
-Moreover, we have the following the statement:\\
+Moreover, we have the following  statement:\\
 $\Pred_{s,t} \land \Pred_1\\
@@
      \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$\\
-The conjunction of the predicate $\Pred_2\subst{\Post_1}$ with the both sides of the implication, we get:\\  
+With the conjunction of the predicate $\Pred_2\subst{\Post_1}$ on both sides of the implication, we get:\\  
 $(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
@@
 $
-Note that  on the right side of the implication we added  the substitution  of $\Post_{OT_x}$ without affecting the validity of the statement, because of the domain independence of the substitution.
+Note that  on the right side of the implication we added  the substitution  of $\Post_{OT_x}$ without affecting the validity of the statement, because  the domain  of the substitution $\Post_{OT_x}$ is disjoint from the others.
 Hence a little rewriting gives:\\
@@
     \forall j\in J_{b}.
-\vis{\beta_{2j}}\!=\!\gamma_{jb}  \Rightarrow \Pred_{OT_{b}}\land \alpha'\!=\!\alpha_2\!
+\vis{\beta_{2j}}\!=\!\gamma_{jb}  \Rightarrow \Pred_{OT_{b}}\land \alpha'\!=\!\alpha_{2 b}\!
 \land \Pred_{s_{21},v_{b}}\subst{\Post_2\uplus\Post_{OT_{b}}})\subst{\Post_1\uplus\Post_{OT_a}})$\\
-Furthermore, the rewriting of the formula gives:\\
+This can be rewritten into:\\
 $(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
@@
 \vis{\beta_{1j}}\!\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-(\vis{\beta_{2j}}\!=\!\gamma_{jb})\subst{\Post_1\uplus\Post_{OT_a}}   \Rightarrow\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_1\uplus\Post_{OT_a}} \land  (\alpha'\!=\!\alpha_{2}) \subst{\Post_1\uplus\Post_{OT_a}} \land \\ \Pred_{s_{21},v_{b}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
-Since $Post_1$  does not act on $\gamma_{jb}$, nor on $ \Pred_{OT_{b}}$ and $  \alpha_{2}$, as well $\Post_{OT_a}$  does not act on $\alpha'$, nor on  $\beta_{2j}$ the formula can be simplified as follows:\\
+(\vis{\beta_{2j}}\!=\!\gamma_{jb})\subst{\Post_1\uplus\Post_{OT_a}}   \Rightarrow\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_1\uplus\Post_{OT_a}} \land  (\alpha'\!=\!\alpha_{2 b}) \subst{\Post_1\uplus\Post_{OT_a}} \land \\ \Pred_{s_{21},v_{b}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
+Since $Post_1$  does not act on $\gamma_{jb}$, nor on $ \Pred_{OT_{b}}$ and $  \alpha_{2}$.
+As well $\Post_{OT_a}$  does not act on $\alpha'$, nor on  $\beta_{2j}$ the formula can be simplified as follows:\\
 $(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
@@
 \vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-\vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jb} \subst{\Post_{OT_a}}  \Rightarrow\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_{OT_a}} \land \alpha'\subst{\Post_1}=\alpha_{2} \subst{\Post_{OT_a}} \land \Pred_{s_{21},v_b}\\\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
+\vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jb} \subst{\Post_{OT_a}}  \Rightarrow\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_{OT_a}} \land \alpha'\subst{\Post_1}=\alpha_{2 b} \subst{\Post_{OT_a}} \land \Pred_{s_{21},v_b}\\\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
 Finally, the conjunction with the term $\Pred_3\subst{\Post_2\shortotimes\Post_1}$ of the both sides of the implication and rewriting, we get:\\
@@
 (\forall j\in J_a.\vis{\beta^1_j}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-\vis{\beta_{2j}}\subst{\Post_1}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}\Rightarrow \Pred_{OT_a}\land\Pred_{OT_{b}}\subst{\Post_{OT_a}} \land  \alpha'\subst{\Post_1}= \alpha_{2} \subst{\Post_{OT_a}} \land (\Pred_{s_{21},v_b} \land  \Pred_3)\\ \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{b}}\shortotimes\Post_{OT_a}})$\\
-Again note that because of the domain independence of the substitution, we removed $\Post_1$ and  we  added the term $\Post_{OT_{b}}\shortotimes\,\Post_{OT_a}$ in the substitution of the right side of the implication.\\
+\vis{\beta_{2j}}\subst{\Post_1}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}\Rightarrow \Pred_{OT_a}\land\Pred_{OT_{b}}\subst{\Post_{OT_a}} \land  \alpha'\subst{\Post_1}= \alpha_{2 b} \subst{\Post_{OT_a}} \land (\Pred_{s_{21},v_b} \land  \Pred_3)\\ \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{b}}\shortotimes\Post_{OT_a}})$\\
+Again note that because of the domain  of the substitution is independent from some predicates and expressions, we removed $\Post_1$ and  we  added the term $\Post_{OT_{b}}\shortotimes\,\Post_{OT_a}$ in the substitution of the right side of the implication.\\
 Finally, by replacing the predicate $(\Pred_{s_{21},v_{b}} \land  \Pred_3)$
@@
    \underbrace{\Pred_{OT_a}\land\Pred_{OT_{b}} \subst{\Post_{OT_a}} \land 
-  \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}}_{\Pred} \land  \underbrace{\alpha'\subst{\Post_1}}_{\alpha}=\underbrace{\alpha_{2} \subst{\Post_{OT_a}}}_{\alpha''} \land\\ \Pred_{s_{31},w_{c}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{c}}\shortotimes \Post_{OT_{b}}\shortotimes\Post_{OT_a}}_{\Post}})$\\
+  \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}}_{\Pred} \land  \underbrace{\alpha'\subst{\Post_1}}_{\alpha}=\underbrace{\alpha_{2 b} \subst{\Post_{OT_a}}}_{\alpha''} \land\\ \Pred_{s_{31},w_{c}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{c}}\shortotimes \Post_{OT_{b}}\shortotimes\Post_{OT_a}}_{\Post}})$\\
  \TODO{Comment passer a ca?}\\

### 2019-06-26 2016-Weak-FH-Bisim/WeakBisim.tex
more indexes and explanations

@@
 
-We let $\gamma$ range over lists of action terms and use $\dotcup$ as the union that appends lists of action terms \TODO{write this properly}. $[a]$ is a list with a single element.
+We let $\gamma$ range over lists of action terms and use $\dotcup$ as the union that appends lists of action terms: given two  lists of action terms  $\gamma\dotcup\gamma '$ concatenates teh two lists.
+The operation is lifted to indexed sets of lists where  $\set {\gamma_1}\dotcup \set {\gamma_2}$ is an indexed set of lists that at each index concatenates the listof  list of $\set{\gamma_1}$ and the one of $\set {\gamma_2}$ (where one of the two lists is empty when $j\not \in \dom(\set{\gamma_1})$).
+$[a]$ is a list with a single element.
 
@@
 $(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} 
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}} \displaystyle{\bigvee_{b\in B}} 
 (\forall j\in J_a.\vis{\beta^1_j}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
@@
   \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}}_{\Pred} \land  \underbrace{\alpha'\subst{\Post_1}}_{\alpha}=\underbrace{\alpha_{2 b} \subst{\Post_{OT_a}}}_{\alpha''} \land\\ \Pred_{s_{31},w_{c}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{c}}\shortotimes \Post_{OT_{b}}\shortotimes\Post_{OT_a}}_{\Post}})$\\
- \TODO{Comment passer a ca?}\\
+The three for all statements (on $J_a$, $J_b$, and $J_c$) can be concatenated using $\dotcup$, the list union lifted to indexed sets.\\
 $\forall j\in J_a\uplus J_b\uplus J_c.

### 2019-06-27 2016-Weak-FH-Bisim/WeakBisim.tex
remarks on implication =>

@@
   \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}}_{\Pred} \land  \underbrace{\alpha'\subst{\Post_1}}_{\alpha}=\underbrace{\alpha_{2 b} \subst{\Post_{OT_a}}}_{\alpha''} \land\\ \Pred_{s_{31},w_{c}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{c}}\shortotimes \Post_{OT_{b}}\shortotimes\Post_{OT_a}}_{\Post}})$\\
-The three for all statements (on $J_a$, $J_b$, and $J_c$) can be concatenated using $\dotcup$, the list union lifted to indexed sets.\\
+The three for all statements (on $J_a$, $J_b$, and $J_c$) can be concatenated using $\dotcup$, the list union lifted to indexed sets (if $\gamma=\gamma'$ and $\gamma''=\gamma'''$ then $\gamma\dotcup\gamma''=\gamma'\dotcup\gamma'''$).\\
 $\forall j\in J_a\uplus J_b\uplus J_c.
@@
 (\forall j\in J.\gamma_j'=\gamma_j \Rightarrow  \Pred \land \alpha=\alpha''  \land \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,}$\\
- This is exactly what we needed to prove. \qed
+\TODO{we miss the other direction no?}
+\qed
 \end{proof}

### 2019-06-27 2016-Weak-FH-Bisim/WeakBisim.tex
both directions for lemma 5

@@
 
-\begin{proof} 
-($\Rightarrow$) First, we prove that Definition \ref{def-Weak-bisim} implies the definition above. In other words,
-Suppose that $\Pred_{s,t}\in \mathcal{R}$ 
+\begin{proof} Note that Definition \ref{def-Weak-bisim} is a particular case of the definition above, thus we only need to prove one direction of the equivalence between the two definition, namely: \\
+($\Rightarrow$) We prove that Definition \ref{def-Weak-bisim} implies the definition above. In other words,
+suppose that $\Pred_{s,t}\in \mathcal{R}$ 
 %and for any open transition $OT$ in $\mathcal{T}_1$:
@@
 (\forall j\in J.\gamma_j'=\gamma_j \Rightarrow  \Pred \land \alpha=\alpha''  \land \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,}$\\
-\TODO{we miss the other direction no?}
 \qed

### 2019-06-27 2016-Weak-FH-Bisim/WeakBisim.tex
finish lemma 5

@@
 (\forall j\in J.\gamma_j'=\gamma_j \Rightarrow  \Pred \land \alpha=\alpha''  \land \Pred_{s',w_{c}}\subst{\Post_{OT}\uplus\Post\,}$\\
-Thus, we can conclude: \TODO{que dire pour passer ici}\\
+
+All the combinations of elements in $A$, $B$, and $C$ provides a set $X$ of weak open transitions (each combination of one transition in $A$, one in $B$, and one in $C$ provides one weak open transition in the set $X$, i.e.
+each $x\in X$ corresponds to a triple $(a,b,c)\in A\times B\times C$); this defines a set of weak open transitions indexed over $X$;  each such open transition leads to a $w_c$ that we call $t_x$.
+This re-indexing allows us to conclude:\\
 $\Pred_{s,t} \land \Pred_{OT}\\

### 2019-06-27 2016-Weak-FH-Bisim/WeakBisim.tex
modif

--- 2019-06-27 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
-We let $\gamma$ range over lists of action terms and use $\dotcup$ as the union that appends lists of action terms: given two  lists of action terms  $\gamma\dotcup\gamma '$ concatenates teh two lists.
-The operation is lifted to indexed sets of lists where  $\set {\gamma_1}\dotcup \set {\gamma_2}$ is an indexed set of lists that at each index concatenates the listof  list of $\set{\gamma_1}$ and the one of $\set {\gamma_2}$ (where one of the two lists is empty when $j\not \in \dom(\set{\gamma_1})$).
-$[a]$ is a list with a single element.
+We let $\gamma$ range over lists of action terms and use $\dotcup$ as the union that appends lists of action terms \TODO{write this properly}. $[a]$ is a list with a single element.
 
@@
 \begin{proof} 
-($\Rightarrow$) First, we prove that Definition \ref{def-Weak-bisim} implies the definition above. In other words,
+($\Rightarrow$) Firstly, we prove that Definition \ref{def-Weak-bisim} implies definition above.\\
 Suppose that $\Pred_{s,t}\in \mathcal{R}$ 
@@
 
-For the sake of simplicity, we prove the rule in the  restricted case where $n$ and $m$ are equal to $1$, hence a single tau open transition will be considered on each side of the potentially visible one.
+For the sake of simplicity, we prove the rule in the  restricted case where $n$ and $m$ to be equal to $1$, hence a single tau open transition will be considered on each side of the potentially visible one.
 The proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule.
@@
            \gamma_{j a}^{j\in J_{a}}, \Pred_{OT_a},\Post_{OT_a}}
-         {u \OTWeakarrow {\alpha_{1 a}} u_a}
+         {u \OTWeakarrow {\alpha_1} u_a}
 \end{mathpar}
- such that  $\forall a, J_{a}=\{j\in J_1'|\beta_{1j}\neq\tau\}, u=t,  (s_{11},u_a|\Pred_{s_{11},u_a})\in \mathcal{R}$ and \\
+ such that  $\forall a, J_{a}=\{j\in J_1'|\beta_{1j}\neq\tau\}, u=t,  (s_{11},t_a|\Pred_{s_{11},u_a})\in \mathcal{R}$ and \\
  $\Pred_{s,t} \land \Pred_1\\
@@
   \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a}
-     \land \alpha_{1 a}\!=\!\tau \land  
+     \land \alpha_1\!=\!\tau \land  
      \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$
 
- Note that, because $\AlgE\cap\AlgA=\emptyset$  (actions and expressions are disjoint) and $\alpha_{1 a}\!=\!\tau$ we have 
-directly ($\alpha_{1 a}$ cannot be a variable, and cannot contain expressions/variables because $\tau$ has no parameter):
+Note that, because $\AlgE\cap\AlgA=\emptyset$  (actions and expressions are disjoint) and $\alpha_x\!=\!\tau$ we have 
+directly ($\alpha_a$ cannot be a variable, and cannot contain expressions/variables because $\tau$ has no parameter):
 \begin{mathpar}
@@
 \end{mathpar}
-%and\\
-%$\Pred_{s,t} \land \Pred_1\\
-%\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
-%  \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a}
-%     \land    \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$
-%
+and//
+$\Pred_{s,t} \land \Pred_1\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
+  \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a}
+     \land    \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$
 
@@
          {
-           \gamma_{j b}^{j\in J_{b}}, \Pred_{OT_{b}},\Post_{OT_{b}}}
-         {u_a \OTWeakarrow {\alpha_{2 b}} v_{b}}
+           \gamma_{b}^{j\in J_{b}}, \Pred_{OT_{b}},\Post_{OT_{b}}}
+         {u_a \OTWeakarrow {\alpha_{2}} v_{b}}
 \end{mathpar}
  such that  $\forall b, J_{b}=\{j\in J_2'|\beta_{2j}\neq\tau\}, 
-(s_{21},v_{b}|\Pred_{s_{21},v_{b}})\in \mathcal{R}$; \\
+(s_{21},v_{y}|\Pred_{s_{21},v_{y}})\in \mathcal{R}$; \\
  $\Pred_{s_{11},u_a} \land \Pred_2\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{b\in B}}
- \!\!  \left( \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}\Rightarrow \Pred_{OT_{b}}\!\land \alpha'\!=\!\alpha_{2 b} \land  
+ \!\!  \left( \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}\Rightarrow \Pred_{OT_{b}}\!\land \alpha'\!=\!\alpha_{2} \land  
      \Pred_{s_{21},v_{b}}\subst{\Post_2\uplus\Post_{OT_{b}}}\right)$
 
-\item Similarly to the case 1, we consider the third  open transition in $\mathcal{T}_1$:
+\item Similarly to the case 1,  the third  open transition in $\mathcal{T}_1$:
      \begin{mathpar}
@@
 \\ 
-\set{\gamma'}=\gamma_{j a}^{j\in J_{a}} \dotcup \gamma_{j b}^{j\in J_{b}} \subst{\Post_{OT_a}} \dotcup\gamma_{jc}^{j\in J_{c}} \subst{\Post_{OT_{ b}}\shortotimes\Post_{OT_a}}\\
+\set{\gamma'}=\gamma_{j a}^{j\in J_{a}} \dotcup \gamma_{jb}^{j\in J_{b}} \subst{\Post_{OT_a}} \dotcup\gamma_{jc}^{j\in J_{c}} \subst{\Post_{OT_{ b}}\shortotimes\Post_{OT_a}}\\
 \Pred=\Pred_{OT_a}\land\Pred_{OT_{b}}\subst{\Post_{OT_a}}\land \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}\\
@@
  \end{mathpar}
-We now need to prove that the following statement holds:\\
+So need to prove that the following statement holds:\\
 $\Pred_{s,t} \land \Pred\\
@@
      \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,})$\\
-     Let's start with the hypothesis \TODO{ je vois pas ce que u=t apporte -- Ludo} and consider  $u=t$   we have:\\
+     Let's start with the hypothesis and consider  $u=t$   we have:\\
 $\Pred_{OT}= \Pred_1 \wedge \Pred_2\subst{\Post_1} \wedge \Pred_3\subst{\Post_2\shortotimes\Post_1}$\\
 $\Post_{OT}=\Post_3\shortotimes \Post_2\shortotimes\Post_1$\\
-Moreover, we have the following  statement:\\
+Moreover, we have the following the statement:\\
 $\Pred_{s,t} \land \Pred_1\\
@@
      \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$\\
-With the conjunction of the predicate $\Pred_2\subst{\Post_1}$ on both sides of the implication, we get:\\  
+The conjunction of the predicate $\Pred_2\subst{\Post_1}$ with the both sides of the implication, we get:\\  
 $(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
@@
 $
-Note that  on the right side of the implication we added  the substitution  of $\Post_{OT_x}$ without affecting the validity of the statement, because  the domain  of the substitution $\Post_{OT_x}$ is disjoint from the others.
+Note that  on the right side of the implication we added  the substitution  of $\Post_{OT_x}$ without affecting the validity of the statement, because of the domain independence of the substitution.
 Hence a little rewriting gives:\\
@@
     \forall j\in J_{b}.
-\vis{\beta_{2j}}\!=\!\gamma_{jb}  \Rightarrow \Pred_{OT_{b}}\land \alpha'\!=\!\alpha_{2 b}\!
+\vis{\beta_{2j}}\!=\!\gamma_{jb}  \Rightarrow \Pred_{OT_{b}}\land \alpha'\!=\!\alpha_2\!
 \land \Pred_{s_{21},v_{b}}\subst{\Post_2\uplus\Post_{OT_{b}}})\subst{\Post_1\uplus\Post_{OT_a}})$\\
-This can be rewritten into:\\
+Furthermore, the rewriting of the formula gives:\\
 $(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
@@
 \vis{\beta_{1j}}\!\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-(\vis{\beta_{2j}}\!=\!\gamma_{jb})\subst{\Post_1\uplus\Post_{OT_a}}   \Rightarrow\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_1\uplus\Post_{OT_a}} \land  (\alpha'\!=\!\alpha_{2 b}) \subst{\Post_1\uplus\Post_{OT_a}} \land \\ \Pred_{s_{21},v_{b}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
-Since $Post_1$  does not act on $\gamma_{jb}$, nor on $ \Pred_{OT_{b}}$ and $  \alpha_{2}$.
-As well $\Post_{OT_a}$  does not act on $\alpha'$, nor on  $\beta_{2j}$ the formula can be simplified as follows:\\
+(\vis{\beta_{2j}}\!=\!\gamma_{jb})\subst{\Post_1\uplus\Post_{OT_a}}   \Rightarrow\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_1\uplus\Post_{OT_a}} \land  (\alpha'\!=\!\alpha_{2}) \subst{\Post_1\uplus\Post_{OT_a}} \land \\ \Pred_{s_{21},v_{b}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
+Since $Post_1$  does not act on $\gamma_{jb}$, nor on $ \Pred_{OT_{b}}$ and $  \alpha_{2}$, as well $\Post_{OT_a}$  does not act on $\alpha'$, nor on  $\beta_{2j}$ the formula can be simplified as follows:\\
 $(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
@@
 \vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-\vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jb} \subst{\Post_{OT_a}}  \Rightarrow\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_{OT_a}} \land \alpha'\subst{\Post_1}=\alpha_{2 b} \subst{\Post_{OT_a}} \land \Pred_{s_{21},v_b}\\\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
+\vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jb} \subst{\Post_{OT_a}}  \Rightarrow\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_{OT_a}} \land \alpha'\subst{\Post_1}=\alpha_{2} \subst{\Post_{OT_a}} \land \Pred_{s_{21},v_b}\\\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
 Finally, the conjunction with the term $\Pred_3\subst{\Post_2\shortotimes\Post_1}$ of the both sides of the implication and rewriting, we get:\\
 $(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}} \displaystyle{\bigvee_{b\in B}} 
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} 
 (\forall j\in J_a.\vis{\beta^1_j}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-\vis{\beta_{2j}}\subst{\Post_1}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}\Rightarrow \Pred_{OT_a}\land\Pred_{OT_{b}}\subst{\Post_{OT_a}} \land  \alpha'\subst{\Post_1}= \alpha_{2 b} \subst{\Post_{OT_a}} \land (\Pred_{s_{21},v_b} \land  \Pred_3)\\ \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{b}}\shortotimes\Post_{OT_a}})$\\
-Again note that because of the domain  of the substitution is independent from some predicates and expressions, we removed $\Post_1$ and  we  added the term $\Post_{OT_{b}}\shortotimes\,\Post_{OT_a}$ in the substitution of the right side of the implication.\\
+\vis{\beta_{2j}}\subst{\Post_1}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}\Rightarrow \Pred_{OT_a}\land\Pred_{OT_{b}}\subst{\Post_{OT_a}} \land  \alpha'\subst{\Post_1}= \alpha_{2} \subst{\Post_{OT_a}} \land (\Pred_{s_{21},v_b} \land  \Pred_3)\\ \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{b}}\shortotimes\Post_{OT_a}})$\\
+Again note that because of the domain independence of the substitution, we removed $\Post_1$ and  we  added the term $\Post_{OT_{b}}\shortotimes\,\Post_{OT_a}$ in the substitution of the right side of the implication.\\
 Finally, by replacing the predicate $(\Pred_{s_{21},v_{b}} \land  \Pred_3)$
@@
    \underbrace{\Pred_{OT_a}\land\Pred_{OT_{b}} \subst{\Post_{OT_a}} \land 
-  \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}}_{\Pred} \land  \underbrace{\alpha'\subst{\Post_1}}_{\alpha}=\underbrace{\alpha_{2 b} \subst{\Post_{OT_a}}}_{\alpha''} \land\\ \Pred_{s_{31},w_{c}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{c}}\shortotimes \Post_{OT_{b}}\shortotimes\Post_{OT_a}}_{\Post}})$\\
-The three for all statements (on $J_a$, $J_b$, and $J_c$) can be concatenated using $\dotcup$, the list union lifted to indexed sets (if $\gamma=\gamma'$ and $\gamma''=\gamma'''$ then $\gamma\dotcup\gamma''=\gamma'\dotcup\gamma'''$).\\
+  \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}}_{\Pred} \land  \underbrace{\alpha'\subst{\Post_1}}_{\alpha}=\underbrace{\alpha_{2} \subst{\Post_{OT_a}}}_{\alpha''} \land\\ \Pred_{s_{31},w_{c}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{c}}\shortotimes \Post_{OT_{b}}\shortotimes\Post_{OT_a}}_{\Post}})$\\
+ \TODO{Comment passer a ca?}\\
 $\forall j\in J_a\uplus J_b\uplus J_c.
@@
 (\forall j\in J.\gamma_j'=\gamma_j \Rightarrow  \Pred \land \alpha=\alpha''  \land \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,}$\\
-\TODO{we miss the other direction no?}
-\qed
+ This is exactly what we needed to prove. \qed
 \end{proof}

### 2019-07-01 2016-Weak-FH-Bisim/WeakBisim.tex
Merged master fixed conflict.
appendix: theorem 10 et intitule lemma 6

--- 2019-06-27 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
-\begin{lemma} The definition of weak bisimulation given in Definition \ref{def-Weak-bisim} is equivalent to the following one:
+\begin{lemma}\label{lem-alternative-weak-bisim} The definition of weak bisimulation given in Definition \ref{def-Weak-bisim} is equivalent to the following one:
 
@@
 
-With the above lemma, we can use the same technique of Theorem \ref{thm-equiv}  to prove that a weak FH-bisimulation is an equivalence.
+With the above lemma, we can use the same technique as for Theorem \ref{thm-equiv}  to prove that a weak FH-bisimulation is an equivalence.
 Indeed, we essentially use the same proof-scheme the main difference concerns  $\beta$ and  $\gamma$.
+Indeed, while the schema of the proof of transitivity was not directly applicable on the definition of weak bisimulation, Lemma~\ref{lem-alternative-weak-bisim} provides a characterisation of weak bisimulation similar to the definition of strong bisimulation, and thus the same proof scheme is directly applicable.
 
@@
 	lemma imply that $Q$ is 
-	not a \pLTS\ but a similar lemma can be proven for a pLTS $Q$}:
+	not a pLTS but a similar lemma can be proven for a pLTS $Q$}:
 	\[ P[Q]_{j_0}  
@@
 		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.  
-		 Then there exist $\gamma_{j_0}=[\beta_0..\beta_n]$, $\Pred\,'$,  
-		$\Post\,'$,   and for all $p\in[0..n]$ there exist $\alpha_p$, $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
+		 Then there exist $n$, $\Pred\,'$,  
+		$\Post\,'$,   and for all $p\in[0..n]$ there exist $\beta_p$, $\alpha_p$, $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
 		%\[
@@
 		}%\]
+\text{\qquad and \qquad}\gamma_{j_0}=[\beta_0..\beta_n]
 	\vspace{-2.2ex}\\\text{and for all $p\in[0..n]$~~}
@@
  \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred = \Pred\,'
-		\land \!\!\bigwedge_{p=0}^n((\alpha_p= \beta_p\land \Pred_p)\bigotimes_{i=0}^{p-1}\Post_i) 
+		\land \!\!\bigwedge_{p=0}^n((\alpha_p= \beta_p\land \Pred_p)\bigotimes_{i=p-1}^{0}\Post_i) 
 \\
@@
 
-\newpage
 \begin{proof} Suppose that we have: 

### 2019-07-03 2016-Weak-FH-Bisim/WeakBisim.tex
indices echanges pendant/apres le skype
Working on lemma 6

@@
 \text{and~}
-\Post=\Post\,' \uplus \bigotimes_{p=0}^n
+\Post=\Post\,' \uplus \bigotimes_{p=n}^0
 		\Post_p  
@@
 			{
-				\gamma_j^{j\in J}, \Pred,  
+				{\gamma_j^{j\in J}}, \Pred,  
 				\Post}
@@
 $\\
-where for all $l\in L$:\\
+where\\
 $\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}}$\\
-$s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
+ for all $l\in L$: $s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
 $\displaystyle{
-\set{\gamma}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!
+\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!
 \Post_{1j}}}\dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }}
@@
 \begin{enumerate}
-\item For each open transition  $\symb{OT}_p$ in the form: 
+\item For each open transition  $\symb{OT}_p$ in the form ($\set{\beta_{1p}}=\beta_{1pj}^{j\in J_{1p}}$): 
 $P[Q]_{j_0}\!\models		
@@
     {
-       \set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
+       {\beta_{1pj}^{j\in J_{1p}}},\Pred_{1p},\Post_{1p}   }
          {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$ \\
@@
 			{
-				(\beta_{1pj})^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
+				(\beta_{1pj})^{j\in (J_{1p}\setminus \Holes(Q)) \cup \{j_0\}}, 
 				{\Pred'_{1p}},  
@@
 			{
-				(\beta_{1pj})^{j\in J\cap\Holes(Q)}, {\Pred''_{1p}},  
+				(\beta_{1pj})^{j\in J_{1p}\cap\Holes(Q)}, {\Pred''_{1p}},  
 				{\Post''_{1p}}}
@@
 			{
-				(\beta_{1pj})^{j\in (J\setminus \Holes(Q)) }, 
+				(\beta_{1pj})^{j\in (J_{1p}\setminus \Holes(Q)) }, 
 				{\Pred'_{1p}},  
@@
 			{\ostate{(s_{p l})^{l\in L\setminus L_Q}} \OTarrow {\tau}
-				\ostate{({s}_{(p+1) l})^{l\in L_Q\setminus L_Q}}}
+				\ostate{({s}_{(p+1) l})^{l\in L\setminus L_Q}}}
 		}$~~and~~ $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}} $
 
-\item Similarly, we use the same process on states named $u$.
-
-\item Finally, for the open transition $\symb{OT}$ in the form: $P[Q]_{j_0}	\models \openrule
-         {
-           \set{\beta_2},\Pred_2,\Post_2 }
+\item Similarly, we have similar open transitions on states $u_{pl}$ (for the final $\tau$ transitions).
+
+\item Finally, for the open transition $\symb{OT}$ in the form ($\set{\beta_{2}}=\beta_{2j}^{j\in J_2}$): $P[Q]_{j_0}	\models \openrule
+         {
+           \beta_{2j}^{j\in J_2},\Pred_2,\Post_2 }
          {\ostate{t} \OTarrow {\alpha} \ostate{t'}}$\\
@@
 			{
-				(\beta_{2j})^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
+				(\beta_{2j})^{j\in (J_2\setminus \Holes(Q)) \cup \{j_0\}}, 
 				{\Pred'_2},  
@@
 			{
-				(\beta_{2j})^{j\in J\cap\Holes(Q)}, {\Pred''_2},  
+				(\beta_{2j})^{j\in J_2\cap\Holes(Q)}, {\Pred''_2},  
 				{\Post''_2}}
@@
 \end{enumerate}
-By using  Lemma \ref{lem-rel-OT-WOT} we can conclude from cases 1, 2 and 3 that we have:
+By using  Lemma \ref{lem-rel-OT-WOT}, denoting $\displaystyle{J=\bigcup_{i=0}^{m_1}J_{1i}\cup J_2\cup \bigcup_{i=0}^{m_2}J_{3i}}$, we can conclude from cases 1, 2 and 3 that we have:
 \begin{mathpar}
@@
 \end{mathpar}
-where for all $l\in L$:\\
+where:\\
 $\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}}$\\
+ for all $l\in L$: 
 $s_l=s_{0l} \wedge s_{(m_1+1)l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)l}=s'_l$
-and $\forall j\in (J\setminus \Holes(Q))\cup \{j_0\}$,\\
-$\set{\gamma}_j=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1ij}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}}\dotcup  \vis{\set{\beta_{2j}}\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}} \dotcup\\
+and \\%$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\}$,\\
+$\set{\gamma}_j=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}} \dotcup\\
 ~~\qquad \mybigdotcup_{i=0}^{m_2}
@@
 
-Concerning $Q$, we consider only the paths for which it moves.
-So for all states for which we have $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}}$, we skip the state $\ostate{({s}_{(p+1) l})^{l\in L_Q}}$ and  we rename all its following states  $\ostate{(s_{p})_l^{l\in L_Q}}$ by $\ostate{({s}_{(p-1) l})^{l\in L_Q}}$.
-We proceed in the same way as for states named $u$.
-To simplify the proof, we consider that in case 3, $Q$  moves, i.e, $\ostate{t_l^{l\in L_Q}} \neq \ostate{t_l'^{\,l\in L_Q}}$, else transition 3 of $Q$ should be skipped and the last $s_{p l}$ are equal to the first $u_{0 l}$.
+Concerning $Q$, we reduce the sequence of OTs to a path for which it moves in all steps.
+In other words, if there is $Q$ does not move at step $q$, then we have $\ostate{s_{q_l}^{l\in L_Q}} = \ostate{{s}_{(q+1) l}^{l\in L_Q}}$ , then we skip the state $\ostate{{s}_{(q+1) l}^{l\in L_Q}}$, i.e.
+we rename all the following states  $\ostate{s_{p l}^{l\in L_Q}}$ where $p\geq q+1$ by $\ostate{{s}_{(p-1) l}^{l\in L_Q}}$.
+Note that if $Q$ does an OT staying at the same state, we keep this necessary OT.
+We proceed in the same way  for states named $u$.
+To simplify the proof, we suppose that in case 3, $Q$  moves, else transition 3 of $Q$ should be skipped and the last $s_{p l}$ are equal to the first $u_{0 l}$.
 So we have: \\
@@
 			{
-				(\beta_{1pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_{1p}}},  
+				(\beta'_{1pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_{1p}}},  
 				{{\Post''_{1p}}}}
@@
 			{
-				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {\Pred''_2},  
+				(\beta'_{2 j})^{j\in J\cap\Holes(Q)}, {\Pred''_2},  
 				{\Post''_2}}
@@
 			{
-				(\beta_{3pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_{3p}}},  
+				(\beta'_{3pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_{3p}}},  
 				{{\Post''_{3p}}}}
@@
 $\\ 
-such that $n_1 \leq m_1$ and $n_2 \leq m_2$\\
+such that $n_1 \leq m_1$ and $n_2 \leq m_2$.\\
 By renaming all state names ($s$, $u$ and $t$) with the same state name $v$. We have:
@@
 			{
-				(\beta_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_p}},  
+				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred''_p}},  
 				{{\Post''_p}}}
@@
 $\\ 
-In this equation, and using cases 1, 2 and 3 above, we have for all $k\in [0\ldots n_1+n_2+2]$, $\beta_{kj_0}=\alpha_k$.
+In this equation, and using cases 1, 2 and 3 above, we have for all $k\in [0\ldots n_1+n_2+2]$, then there is an action $\beta$ such that $\beta=\beta_{1p j_0}$ s.t.
+$j_0\in J_{1p}$, or $\beta=\beta_{2 j_0}$ with $j_0\in J_{2}$, or $\beta=\beta_{3p j_0}$ s.t.
+$j_0\in J_{3p}$, where $\beta=\alpha_k$, additionally the different $\beta$ are ordered by following the OTs, somehow performing the same re-indexing as  the removal of steps where $Q$ does not move above.
+Overall we have\footnote{under the assumption written above, i.e.
+that $Q$ moves in the middle OT, i.e.
+$j_0\in J_{2}$}:
+\[
+[\beta_{1 p j_0}|j_0\in J_{1p}]\dotcup [\beta_{2 j_0}] \dotcup [\beta_{3 p j_0}|j_0\in J_{3p}] = [\alpha_0..\alpha_{n_1+n_2+2}]
+\]
 
@@
 By considering $\tau$  actions we split the sequence of actions into $n$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.
-We can decompose each of the $n$ subsequences; the length of the subsequence number $k$ is $n_k$,  and the subsequence is made of the following OTs:\\
-$\forall p\! \in\! [0..(n_k\!-\!1)] Q\models{\openrule
-			{
-				(\beta_{1pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_{1p}}},  
-				{{\Post''_{1p}}}}
+We can decompose each of the $n$ subsequences; for $k\in [1..n]$ the position of the $k^{\text{th}}$ visible action is is $n_k$, $k\in [1..n-1]$ for  $n'_k$ is any index between $n_k$ and $n_{k+1}$,  $n'_0=0$ and $n'_n=n_1+n_2+3$.
+We obtain $n$ subsequences  made of the following OTs, for all $k\in [1..n]$ :\\
+$\forall p\! \in\! [n'_{k-1}..(n_k\!-\!1)] Q\models{\openrule
+			{
+				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred''_{p}}},  
+				{{\Post''_{p}}}}
 				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
@@
 			{
-				(\beta_{2j})^{j\in J\cap\Holes(Q)}, {{\Pred''_2}},  
-				{{\Post''_2}}}
-				{\ostate{v_{n_kl}^{l\in L_Q}} \OTarrow {\alpha_k}
+				\beta_{n_k j}^{j\in J\cap\Holes(Q)}, {{\Pred''_{n_k}}},  
+				{{\Post''_{n_k}}}}
+				{\ostate{v_{n_kl}^{l\in L_Q}} \OTarrow {\alpha_{{n_k}}}
 				\ostate{v_{(n_k+1)l}^{l\in L_Q}}}
@@
 			{
-				(\beta^3_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_{3p}}},  
-				{{\Post''_{3p}}}}
+				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred''_{p}}},  
+				{{\Post''_{p}}}}
 				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
@@
 			{\ostate{v_{l}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
-				\ostate{v_{l}'^{l\in L_Q}}}
+				\ostate{(v_{l}')^{l\in L_Q}}}
 		}%\]
 \end{mathpar}
-$\alpha_k'=\alpha_k\displaystyle{\subst{\bigotimes_{j=0}^{(n_k-1)}\!\!\Post''_{1j}}}$\\
-$\forall l \in L_Q. v_l=v_{0l} \wedge v_l'=v_{n_kl}$, 
-$\forall j \in  (J\cap\Holes(Q)),\,$\\
-$\displaystyle{\gamma_{kj} }=\displaystyle{\mybigdotcup_{i=0}^{n_k-1} \vis{\set{\beta_{1ij}}\subst{\bigotimes_{j=i-1}^{0}\!\!\!\Post''_{1j}}}\dotcup \vis{\set{\beta_{2j}}\subst{\bigotimes_{j=n_k-1}^{0}\!\!\!\Post''_{1j}}}} \dotcup\\
+$\alpha_k'=\alpha_k\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'{k-1}}\!\!\Post''_{p}}}$\\
+$\forall l \in L_Q. v_l=v_{(n'_{k-1})l} \wedge v_l'=v_{(n'_k-1)l}$, \\
+$\forall j \in  (J\cap\Holes(Q)),\,$
+$\displaystyle{\gamma_{kj} }=\displaystyle{\mybigdotcup_{i=n_k-1}^{0} \vis{\set{\beta_{1ij}}\subst{\bigotimes_{j=i-1}^{0}\!\!\!\Post''_{1j}}}\dotcup \vis{\set{\beta_{2j}}\subst{\bigotimes_{j=0}^{n_k-1}\!\!\!\Post''_{1j}}}} \dotcup\\
 ~~\qquad \mybigdotcup_{i=n_k+1}^{n_k'-1}

### 2019-07-04 2016-Weak-FH-Bisim/WeakBisim.tex
finished the equations page 49
Bug lemma 6
current proof state
premiere passe notation lemma 7
working on proof of lemma 6

@@
  \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred = \Pred\,'
-		\land \!\!\bigwedge_{p=0}^n((\alpha_p= \beta_p\land \Pred_p)\bigotimes_{i=p-1}^{0}\Post_i) 
+		\land \!\!\bigwedge_{p=0}^n((\alpha_p\bigotimes_{i=p-1}^{0}\Post_i) = \beta_p\land (\Pred_p\bigotimes_{i=p-1}^{0}\Post_i) )
 \\
@@
 			{
-				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
+				(\gamma_j')^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
 				\Pred\,',  
@@
 and \\%$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\}$,\\
-$\set{\gamma}_j=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}} \dotcup\\
+${(\gamma_j')}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}} \dotcup\\
 ~~\qquad \mybigdotcup_{i=0}^{m_2}
@@
 \Post'=\bigotimes_{j=m_2}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}$
+
+Note that for all $j\in J\setminus \Holes(Q)$, $\gamma_j' = \gamma_j$ because for all $l$ $\Post'_{1l}$ coincide with $\Post_{1l}$ on the variables of $\beta_{1ij}$, and similarly for $\Post'_2$ and $\Post'_{3l}$.
+%Concerning $\gamma'_{j_0}$ we have:
+%\[\gamma'_{j_0}=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{{\alpha_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}} \dotcup\\
+%~~\qquad \mybigdotcup_{i=0}^{m_2}
+%\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}} }\]
 
@@
 			{
-				(\beta'_{1pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_{1p}}},  
+				(\beta_{1p})^{j\in J\cap\Holes(Q)}, {{\Pred''_{1p}}},  
 				{{\Post''_{1p}}}}
@@
 $\\ 
-In this equation, and using cases 1, 2 and 3 above, we have for all $k\in [0\ldots n_1+n_2+2]$, then there is an action $\beta$ such that $\beta=\beta_{1p j_0}$ s.t.
+In this equation, and using case 1 above for all $k\in [0\ldots n_1]$ there is a $p$ (following the re-indexing done in the removal of steps where $Q$ does not move) $\Pred_{1p}\implies \alpha_{1p}=\beta_{1 p j_0}=\alpha_k$ and thus $\Pred_{1p}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\implies \beta_{1 p j_0}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}=\alpha_k\subst{\bigotimes_{j=i-1}^{0}\!\!\Post''_{1j}}$ (because $\beta_{1 p j_0}$ only contains variables of $P$ and $\alpha_k$ only variables of $Q$).
+Finally because $\Post''_{1j}$ is only definesd when $Q$ moves:
+\[\Pred_{1p}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\implies
+ \beta_{1 p j_0}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}=\alpha_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post''_{j}}\]
+We have similar equations for $\alpha_{n_1+1}$ related with $\beta_{2 j_0}$ and the following $\alpha_k$ related with $\beta_{3 j_0}$ for some $p$.
+Note that the substitutions are however more complex.
+\TODO{detailler les equations?}
+
+Overall we obtain (we skip here the details about the three cases 1, 2, and 3 above that all fall into the same equation because of the re-indexing we perform) \[\Pred \implies \gamma_{j_0}=
+\vis{[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post''_{j}}|p\in[0..n_1+n_2+2]]}\]
+
+%, 2 and 3 above, we have for all $k\in [0\ldots n_1+n_2+2]$, then there is an action $\beta$ such that $\beta=\beta_{1p j_0}$ s.t.
 $j_0\in J_{1p}$, or $\beta=\beta_{2 j_0}$ with $j_0\in J_{2}$, or $\beta=\beta_{3p j_0}$ s.t.
@@
 $j_0\in J_{2}$}:
-\[
-[\beta_{1 p j_0}|j_0\in J_{1p}]\dotcup [\beta_{2 j_0}] \dotcup [\beta_{3 p j_0}|j_0\in J_{3p}] = [\alpha_0..\alpha_{n_1+n_2+2}]
-\]
+%\[ \Pred_* \implies
+%[\beta_{1 p j_0}|j_0\in J_{1p}]\dotcup [\beta_{2 j_0}] \dotcup [\beta_{3 p j_0}|j_0\in J_{3p}] = [\alpha_0..\alpha_{n_1+n_2+2}]
+%\]
+%
+%And thus \[\gamma_{j_0} = []\]
 
@@
 \end{mathpar}
-$\alpha_k'=\alpha_k\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'{k-1}}\!\!\Post''_{p}}}$\\
+$\alpha_k'=\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k-1}}\!\!\Post''_{p}}}$\\
 $\forall l \in L_Q. v_l=v_{(n'_{k-1})l} \wedge v_l'=v_{(n'_k-1)l}$, \\
-$\forall j \in  (J\cap\Holes(Q)),\,$
-$\displaystyle{\gamma_{kj} }=\displaystyle{\mybigdotcup_{i=n_k-1}^{0} \vis{\set{\beta_{1ij}}\subst{\bigotimes_{j=i-1}^{0}\!\!\!\Post''_{1j}}}\dotcup \vis{\set{\beta_{2j}}\subst{\bigotimes_{j=0}^{n_k-1}\!\!\!\Post''_{1j}}}} \dotcup\\
+$\displaystyle{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=\displaystyle{\mybigdotcup_{i=n'_{k-1}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k-1}}\!\!\!\Post''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k-1}}\!\!\!\Post''_{l}}}} \dotcup\\
 ~~\qquad \mybigdotcup_{i=n_k+1}^{n_k'-1}
-\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\!\!\bigotimes_{j=n_k-1}^{0}\!\!\!\Post''_{1j}} }\\
-\Pred_k=\bigwedge_{i=0}^{n_k-1}\!\!\Pred''_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred''_2 \subst{\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{1j}}\land\\ 
-~\qquad\quad\bigwedge_{i=n_k+1}^{n_k'-1}\!\!\!\Pred''_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\!\!\bigotimes_{j=n_k-1}^{0}\!\!\!\Post''_{1j}}\\
-\Post_k= \bigotimes_{j=n_k'-1}^{0}\!\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\!\!\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{1j}$\\
-
-In this case, the number of weak open transitions
-might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.\\
-We have: 
-$\displaystyle{\gamma_{j_0}}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta_{1i{j_0}}} \dotcup  \vis{\set{\beta_{2i}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3i{j_0}}}$. Additionally, we have
-$[\alpha'_0..
-\alpha'_n]$ is a a list of $\alpha_p$ such that $p\in [0..(n_1\!+\!n_2\!+\!2)] \land \alpha_p\neq \tau$ where for all $k\in [0\ldots n_1+n_2+2]$, $\beta_{kj_0}=\alpha_k$.
-In other words, $\displaystyle{\mybigdotcup_{i=0}^{m_1}  \vis{\beta_{1i{j_0}}} \dotcup  \vis{\set{\beta_{2i}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3i{j_0}}} = [\alpha'_0..
+\vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}} \subst{\bigotimes_{l=i-1}^{n_k\!+\!1}\!\Post''_{l}\shortotimes\Post''_{n_k}\shortotimes\!\!\bigotimes_{l=n_k-1}^{n'_{k-1}}\!\!\!\Post''_{l}} }\\
+%
+\Pred_k=\bigwedge_{i=n'_{k-1}}^{n_k\!-\!1}\!\!\Pred''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k-1}}\!\!\Post_{j}}\land\Pred''_{n_k} \subst{\bigotimes_{j=n_k-1}^{n'_{k-1}}\!\!\Post''_{j}}\land\\ 
+~\qquad\quad\bigwedge_{i=n_k+1}^{n_k'-1}\!\!\!\Pred''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k-1}}\!\!\!\Post''_{j}\shortotimes\Post''_{n_k}\shortotimes\!\!\bigotimes_{j=n_k-1}^{n'_{k-1}}\!\!\!\Post''_{j}}
+\\
+\Post_k= \bigotimes_{j=n_k'-1}^{n'_{k-1}}\!\!\Post''_{j}$\\
+
+%In this case, the number of weak open transitions
+%might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.\\
+Note that \[\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{p}}} = \alpha_k'\displaystyle{\subst{\bigotimes_{j=n'_{k-1}}^{0}\!\!\Post''_{p}}} = 
+\alpha_k'\displaystyle{\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{p}}}\]
+We now have: \TODO{add ref to eq 1 page above?}
+\[\Pred \implies \gamma_{j_0}=
+\vis{[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[1..n]]}\]
+
+%$\displaystyle{\gamma_{j_0}}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta_{1i{j_0}}} \dotcup  \vis{{\beta_{2j_0}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3i{j_0}}}$. Additionally, we have
+%$[\alpha'_0.. \alpha'_n]$ is the list of non-$\tau$ $\alpha_p$.
+%% such that $p\in [0..(n_1\!+\!n_2\!+\!2)] \land \alpha_p\neq \tau$ where for all $k\in [0\ldots n_1+n_2+2]$, $\beta_{kj_0}=\alpha_k$. 
+%In other words, $\displaystyle{\mybigdotcup_{i=0}^{m_1}  \vis{\beta_{1i{j_0}}} \dotcup  \vis{{\beta_{2j_0}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3i{j_0}}} = [\alpha'_0..
 \alpha'_n]}$.
-This ensures that $\gamma_{j_0}=[\alpha'_0..
+%This ensures that $\gamma_{j_0}=[\alpha'_0..
 \alpha'_n]$.
+%
+%
+%Consequently
 
@@
 
-Consequently, for  $\gamma_{j_0}=[\beta_0..\beta_n]$ such that $\beta_i=\alpha'_i$ we have $n$ weak open transitions  $\symb{WOT}_k$ such that $k\in [0..n]$.
-Therefore, we can conclude that we have for all $k\in [0..n]$:  
+\TODO{stopped here not sure about the following}
+
+Consequently, we have $n$ weak open transitions  $\symb{WOT}_k$ such that $k\in [1..n]$.
+Therefore, we can conclude that we have for all $k\in [1..n]$:  
 \begin{mathpar}

### 2019-07-05 2016-Weak-FH-Bisim/WeakBisim.tex
just notation

@@
 %\hspace{1cm}
- $\bigvee_{x\in X}
+ $\displaystyle{\bigvee_{x\in X}
    \left( \forall j. \beta_j=\beta_{jx}  \land \Pred_{OT_x}
      \land \alpha\!=\!\alpha_x \land  
-     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)$
+     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}$
      %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
@@
  $\Pred \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-   \left( \forall j\in J_x. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
-     \land \alpha\!=\!\alpha_x \land  
-     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)$
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
+   \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \Rightarrow\! \Pred_{OT_x}
+     \!\land\! \alpha\!=\!\alpha_x\! \land\!  
+     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}$
 
@@
        	$\mathcal{T}_2$ relating $s$ and $u$, let $(t_p)^{p\in P}$ be this family.  
-       	       	We have $\Pred_{s,u} = \bigvee_{p\in P} \Pred_{s,p}\land\Pred_{p,u}$.
+       	       	We have $\Pred_{s,u} = \displaystyle{\bigvee_{p\in P} \Pred_{s,p}\land\Pred_{p,u}}$.
 
@@
        	$\Pred_{s,p} \land \Pred_{OT}\\
-       	\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
+       	\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}
        	\left( \forall j. \beta_j=\beta_{jpx}  \Rightarrow \Pred_{OT_{px}}
        	\land \alpha\!=\!\alpha_{px} \land
-       	\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\right)$\\
+       	\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\right)}$\\
 
@@
        	$\Pred\,'_{p,u} \land \Pred_{OT_{p x}}\\
-       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
-       	\left( \forall j. \beta_{jpx}=\beta_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
-       	\land \alpha_{px}\!=\!\alpha_{pxy} \land
-       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}\right)$.\\
+       	\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}\!
+       	\left( \forall j.\beta_{jpx}\!=\!\beta_{jpxy} \Rightarrow\! \Pred_{OT_{pxy}}\!
+       	\land\! \alpha_{px}\!=\!\alpha_{pxy} \!\land\!
+       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}\!\uplus\!\Post_{OT_{pxy}}}\right)}$\\
 
@@
        		$\Pred_{s,u} \land \Pred_{OT}\\
-       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
+       		\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
        		\left( \forall j. \beta_j=\beta_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
        		\land \alpha\!=\!\alpha_{pxy} \land
-       		\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{pxy}}}\right)$.
+       		\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{pxy}}}\right)}$.
        	\end{small}
@@
        		$\Pred_{s,p} \land \Pred_{OT}\land\Pred_{p,u}\\
-       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
+       		\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}
        		\left( \forall j. \beta_j=\beta_{jpx}  \Rightarrow \Pred_{OT_{px}}
        		\land \alpha\!=\!\alpha_{px} \land
-       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\right)\land\Pred_{p,u}\\
+       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\right)\land\Pred_{p,u}}\\
        		%
@@
        		\big( \forall j'. \beta_{j'px}=\beta_{j'pxy}  \Rightarrow \Pred_{OT_{pxy}}
-       		\land \alpha_{px}\!=\!\alpha_{pxy}\\\hspace{3em}~ \land
+       		\land \alpha_{px}\!=\!\alpha_{pxy}\\~\hspace{3em}~ \land
        		\Pred_{{pxy}}\subst{\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}\big))
@@
        		\Pred_{OT_{pxy}}
-       		\land \alpha\!=\alpha_{px}\!=\!\alpha_{pxy}\\\hspace{3em}~ \land
+       		\land \alpha\!=\alpha_{px}\!=\!\alpha_{pxy}\\~\hspace{3.5em}~ \land
        		\Pred_{{pxy}}\subst{\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}
@@
       	\begin{small}     	
-$\Pred_{s,u} \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \bigvee_{p\in P} (
+$\displaystyle{\Pred_{s,u} \land \Pred_{OT}}\\
+ \implies\!\!\! \bigvee_{p\in P} (
 	\Pred_{s,p}\land\Pred_{p,u} \land \Pred_{OT})\\
@@
  \bigvee_{x\in X} \bigvee_{y\in Y}
-\big( \forall j, j'. \beta_j=\beta_{jpx} \land \beta_{j'px}=\beta_{j'pxy}
-\Rightarrow \big( 
+\big( \forall j, j'.\beta_j=\beta_{jpx} \land \beta_{j'px}=\beta_{j'pxy}
+\Rightarrow\\ ~\hspace{7em} 
 \Pred_{OT_{pxy}}
-\land \alpha\!=\alpha_{px}\!=\!\alpha_{pxy}\\~\hspace{3em}~ \land
-\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{pxy}}}\big)\big)
+\land \alpha\!=\!\alpha_{px}\!=\!\alpha_{pxy}\land\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus \Post_{OT_{pxy}}}\big)
 \\
 \hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
-\left( \forall j. \beta_j=\beta_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
+\left( \forall j. \beta_j\!=\!\beta_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
 \land \alpha\!=\!\alpha_{pxy} \land
-\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{pxy}}}\right)$.
+\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{pxy}}}\right)$
   \end{small}
@@
 
-   \begin{small}\begin{proof}
+   \begin{proof}
 Consider rule \TrDeux\ in 
@@
 	\noindent
+\begin{small}	
 \begin{mathpar}
@@
 \end{mathpar}
+
+\end{small}
 %\begin{mathpar}
@@
 \{j_0\}$; we denote $I'_1=I_1\setminus \{j_0\}$ the predicate is 
-$\Pred\,'=\bigwedge_{m\in I_1'\uplus I_2}\Pred_m  \land \Predsv(SV_k,\alpha_m^{m \in I'_1\uplus I_2},\beta_j^{j\in J\cup \{j_0\}},\alpha)$
+$\displaystyle{\Pred\,'=\!\!\!\!\!\bigwedge_{m\in I_1'\uplus I_2}\!\!\!\!\!\Pred_m  \land \Predsv(SV_k,\alpha_m^{m \in I'_1\uplus I_2},\beta_j^{j\in J\cup \{j_0\}},\alpha)}$
 where\footnotemark[\thefootnote] $\Predsv(SV_k,\alpha_m^{m \in I'_1\uplus I_2},\beta_j^{j\in 
@@
 	\noindent
+	\begin{small}
 \begin{mathpar}
@@
 \end{mathpar}
+ \end{small}
 \qed
@@
 \end{proof}
-   \end{small}
 
@@
 does not appear neither as global action nor as an action of a hole.
-\begin{small}
 
@@
 \end{mathpar}  
-
+\end{small}
 We know each premise is \True\ for $P$ and try to prove the equivalent premise for 
@@
 predicate for the open 
-transition is: $\Pred\,''=\bigwedge_{m\in I _1\uplus I_2}\Pred_m \land \Pred\,'
+transition is: $\displaystyle{\Pred\,''=\!\!\!\!\bigwedge_{m\in I _1\uplus I_2}\!\!\!\Pred_m \land \Pred\,'
 \land \Pred(SV_k,v_i^{i\in I_1\uplus I_2}\uplus(j_0\mapsto v_Q),\beta_j^{j\in 
-J},\alpha)$. 
+J},\alpha)}$. 
 By definition 
@@
 	gathers the post-conditions related to all 
-	the leaves: $\biguplus_{m\in I_1\cup\{j_0\}\uplus I_2} 
-    		\Post_m = 	\Post\uplus \Post\,'$. Finally, the composed open transition can be
+	the leaves: $\displaystyle{\biguplus_{m\in I_1\cup\{j_0\}\uplus I_2} 
+    		\!\!\!\!\!\Post_m = 	\Post\uplus \Post\,'}$. Finally, the composed open transition can be
         built by \TrDeux:
@@
 \end{mathpar}  
+\end{small}
  \qed
         \end{proof}
-\end{small}
 
@@
  $\Pred_{s,t} \land \Pred\,''
- \Rightarrow \bigvee_{x\in X}
+ \Rightarrow \displaystyle{\bigvee_{x\in X}
  \left( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \Rightarrow 
@@
  \land \alpha_Q\!=\!\alpha_x \land  
- \Pred_{s x}\subst{\Post\,''\uplus\Post_{OT_x}}\right)$
+ \Pred_{s x}\subst{\Post\,''\uplus\Post_{OT_x}}\right)}$
 
@@
 			and  \\
-			$\Pred_{s,t} \land \Pred\,'
+			$\displaystyle{\Pred_{s,t} \land \Pred\,'
 		 \Rightarrow \bigvee_{x\in X}
@@
 			\land \alpha\!=\!\alpha_x \land  
-			\Pred_{s x}\subst{\Post\,'\uplus\Post_{OT_x}}\right)$
+			\Pred_{s x}\subst{\Post\,'\uplus\Post_{OT_x}}\right)}$
 			%     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x}) \right)$.
@@
 \\
-\Pred_Q=\bigwedge_{h=0}^{k}\!\big(\Pred^1_h\bigotimes_{j=0}^{h-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{h=0}^{k}\subst{\Post_h^1}\land \bigwedge_{h=0}^{k'}\!\Pred_h^3\big(\bigotimes_{j=0}^{h-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{h=0}^{k}\subst{\Post_h^1}\big)
+\Pred_Q=\bigwedge_{h=0}^{k}\!\big(\Pred^1_h\bigotimes_{j=h-1}^{0}\subst{\Post_j^1}\big)\land \Pred^2\bigotimes_{h=k}^{0}\subst{\Post_h^1}\land\\~\qquad\qquad \bigwedge_{h=0}^{k'}\!\Pred_h^3\big(\bigotimes_{j=h-1}^{0}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{h=k}^{0}\subst{\Post_h^1}\big)
 \\
-\Post_Q=\bigotimes_{h=0}^{k'}\Post^3_h\subst{\Post^2}\bigotimes_{j=0}^{k}\subst{\Post^1_j}
+\Post_Q=\bigotimes_{h=k'}^{0}\Post^3_h\subst{\Post^2}\bigotimes_{j=k}^{0}\subst{\Post^1_j}
 $
@@
 \[
-\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred^1_h}\subst{\bigotimes_{i=0}^{h-1}\Post_i^1}\land
-\left(Pred\land\Pred^2\land \alpha_Q=\beta_{j_0 }\right)\subst{\bigotimes_{i=0}^{k}{\Post_i^1}}\land\\\displaystyle
-\bigwedge_{h=0}^{k'}{\Pred^3_h}\subst{\bigotimes_{i=0}^{h-1}{\Post_i^3}\shortotimes({\Post\uplus \Post^2})\shortotimes\bigotimes_{i=0}^{k}{\Post_i^1}}
+\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred^1_h}\subst{\bigotimes_{i=h-1}^{0}\Post_i^1}\land
+\left(Pred\land\Pred^2\land \alpha_Q=\beta_{j_0 }\right)\subst{\bigotimes_{i=k}^{0}{\Post_i^1}}\land\\\displaystyle
+\bigwedge_{h=0}^{k'}{\Pred^3_h}\subst{\bigotimes_{i=h-1}^{0}{\Post_i^3}\shortotimes({\Post\uplus \Post^2})\shortotimes\bigotimes_{i=k}^{0}{\Post_i^1}}
 \end{array}
@@
 
-\[\Post_c=(\bigotimes_{i=0}^{k'}{\Post_i^3})\shortotimes({\Post\uplus \Post^2})\shortotimes\bigotimes_{i=0}^{k}{\Post_i^1}
+\[\Post_c=(\bigotimes_{i=k'}^{0}{\Post_i^3})\shortotimes({\Post\uplus \Post^2})\shortotimes\bigotimes_{i=k}^{0}{\Post_i^1}
 \]
@@
 \qquad
-\Pred\,'=\Pred\land \bigwedge_{t=0}^{n}(\alpha_t=\beta_t\land \Pred_t)\bigotimes_{i=0}^{t-1}\Post_i
+\Pred\,'=\Pred\land \bigwedge_{t=0}^{n}(\alpha_t=\beta_t\land \Pred_t)\bigotimes_{i=t-1}^{0}\Post_i
 \\
 \forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
-\Post\,'=\Post\uplus\bigotimes_{t=0}^{n}
+\Post\,'=\Post\uplus\bigotimes_{t=n}^{0}
 		\Post_t
@@
 $\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{p=0}^{m_1} \vis{\set{\beta^1_p}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{p=0}^{m_2} \vis{\set{\beta^3_p}}}\\
-\Pred=\bigwedge_{p=0}^{m_1}\!\big(\Pred^1_p\bigotimes_{j=0}^{p-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{p=0}^{m_1}\subst{\Post_p^1}\land \bigwedge_{p=0}^{m_2}\!\Pred_p^3\big(\bigotimes_{j=0}^{p-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{p=0}^{m_1}\subst{\Post_p^1}\big)\\
-\Post=\bigotimes_{p=0}^{m_2}\Post^3_p\subst{\Post^2}\bigotimes_{j=0}^{m_1}\subst{\Post^1_j}
+\Pred=\bigwedge_{p=0}^{m_1}\!\big(\Pred^1_p\bigotimes_{j=p-1}^{0}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{p=m_1}^{0}\subst{\Post_p^1}\land \bigwedge_{p=0}^{m_2}\!\Pred_p^3\big(\!\!\bigotimes_{j=p-1}^{0}\subst{\Post^3_j}\subst{\Post^2}\!\!
+\bigotimes_{p=m_1}^{0}\subst{\Post_p^1}\big)\\
+\Post=\bigotimes_{p=m_2}^{0}\Post^3_p\subst{\Post^2}\bigotimes_{j=m_1}^{0}\subst{\Post^1_j}
 $\\
@@
 $\displaystyle{\gamma_{t j}^{j\in J_t}=\mybigdotcup_{h=0}^{k} \vis{\set{\beta^1_h}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{h=0}^{k'} \vis{\set{\beta^3_h}}}\\
-\Pred_t=\bigwedge_{h=0}^{k}\!\big(\Pred^1_h\bigotimes_{j=0}^{h-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{h=0}^{k}\subst{\Post_h^1}\land \bigwedge_{h=0}^{k'}\!\Pred_h^3\big(\bigotimes_{j=0}^{h-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{h=0}^{k}\subst{\Post_h^1}\big)\\
-\Post=\bigotimes_{h=0}^{k'}\Post^3_h\subst{\Post^2}\bigotimes_{j=0}^{k}\subst{\Post^1_j}
+\Pred_t=\bigwedge_{h=0}^{k}\!\big(\Pred^1_h\bigotimes_{j=h-1}^{0}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{h=k}^{0}\subst{\Post_h^1}\land \bigwedge_{h=0}^{k'}\!\Pred_h^3\big(\bigotimes_{j=h-1}^{0}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{h=k}^{0}\subst{\Post_h^1}\big)\\
+\Post=\bigotimes_{h=k'}^{0}\Post^3_h\subst{\Post^2}\bigotimes_{j=k}^{0}\subst{\Post^1_j}
 $
@@
 \[
-\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred^1_h}\subst{\bigotimes_{i=0}^{h-1}\Post_i^1}\land
-\left(Pred_p\land\Pred^2\land \alpha_t=\beta^i_{p j_0 }\right)\subst{\bigotimes_{i=0}^{k}{\Post_i^1}}\land\\\displaystyle
-\bigwedge_{h=0}^{k'}{\Pred^3_h}\subst{\bigotimes_{i=0}^{h-1}{\Post_i^3}\shortotimes({\Post_p\uplus \Post^2})\shortotimes\bigotimes_{i=0}^{k}{\Post_i^1}}
+\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred^1_h}\subst{\bigotimes_{i=h-1}^{0}\Post_i^1}\land
+\left(Pred_p\land\Pred^2\land \alpha_t=\beta^i_{p j_0 }\right)\subst{\bigotimes_{i=k}^{0}{\Post_i^1}}\land\\\displaystyle
+\bigwedge_{h=0}^{k'}{\Pred^3_h}\subst{\bigotimes_{i=h-1}^{0}{\Post_i^3}\shortotimes({\Post_p\uplus \Post^2})\shortotimes\bigotimes_{i=k}^{0}{\Post_i^1}}
 \end{array}
@@
 
-\[\Post_c=(\bigotimes_{i=0}^{k'}{\Post_i^3})\shortotimes({\Post_p\uplus \Post^2})\shortotimes\bigotimes_{i=0}^{k}{\Post_i^1}
+\[\Post_c=(\bigotimes_{i=k'}^{0}{\Post_i^3})\shortotimes({\Post_p\uplus \Post^2})\shortotimes\bigotimes_{i=k}^{0}{\Post_i^1}
 \]

### 2019-07-05 2016-Weak-FH-Bisim/WeakBisim.tex
in lemma 6 again
skype meeting

@@
  \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred = \Pred\,'
-		\land \!\!\bigwedge_{p=0}^n((\alpha_p\bigotimes_{i=p-1}^{0}\Post_i) = \beta_p\land (\Pred_p\bigotimes_{i=p-1}^{0}\Post_i) )
+		\land \!\!\bigwedge_{p=0}^n((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} )
 \\
@@
 
+We denote the following predicate (we will need it for reasoning on the global predicate and will reason on it along the proof):
+\[\begin{array}{l}\displaystyle{
+\Pred_\beta=\bigwedge_{p=0}^{m_1}(\beta_{1pj_0}=\alpha_{1p})\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}} \wedge (\beta_{2j_0}=\alpha_2)\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}}\\\quad
+\displaystyle{
+\wedge\bigwedge_{p=0}^{m_2}(\beta_{3pj_0}=\alpha_{3p})
+\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}}
+\end{array}\]
+
 Concerning $Q$, we reduce the sequence of OTs to a path for which it moves in all steps.
@@
 			{
-				(\beta_{1p})^{j\in J\cap\Holes(Q)}, {{\Pred''_{1p}}},  
+				(\beta_{1pj}')^{j\in J\cap\Holes(Q)}, {{\Pred''_{1p}}},  
 				{{\Post''_{1p}}}}
@@
 $\\ 
-In this equation, and using case 1 above for all $k\in [0\ldots n_1]$ there is a $p$ (following the re-indexing done in the removal of steps where $Q$ does not move) $\Pred_{1p}\implies \alpha_{1p}=\beta_{1 p j_0}=\alpha_k$ and thus $\Pred_{1p}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\implies \beta_{1 p j_0}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}=\alpha_k\subst{\bigotimes_{j=i-1}^{0}\!\!\Post''_{1j}}$ (because $\beta_{1 p j_0}$ only contains variables of $P$ and $\alpha_k$ only variables of $Q$).
-Finally because $\Post''_{1j}$ is only definesd when $Q$ moves:
-\[\Pred_{1p}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\implies
+In this equation, and using case 1 above for all $k\in [0\ldots n_1]$ there is a $p\in [0..m_1]$ (following the re-indexing done in the removal of steps where $Q$ does not move) $\Pred_{1p}$ contains $ \alpha_{1p}=\beta_{1 p j_0}$ with $\alpha_{1p}=\alpha_k$.
+Because $\beta_{1 p j_0}$ only contains variables of $P$ and $\alpha_k$ only variables of $Q$:
+\[(\alpha_{1p}=\beta_{1pj_0})\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\iff
  \beta_{1 p j_0}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}=\alpha_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post''_{j}}\]
@@
 
-Overall we obtain (we skip here the details about the three cases 1, 2, and 3 above that all fall into the same equation because of the re-indexing we perform) \[\Pred \implies \gamma_{j_0}=
+Overall we obtain (we skip here the details about the three cases 1, 2, and 3 above that all fall into the same equation because of the re-indexing we perform) \[\Pred_\beta \iff \gamma_{j_0}=
 \vis{[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post''_{j}}|p\in[0..n_1+n_2+2]]}\]
@@
 				{{\Post_k}}}
-			{\ostate{v_{l}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
-				\ostate{(v_{l}')^{l\in L_Q}}}
+			{\ostate{v_{kl}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
+				\ostate{(v_{kl}')^{l\in L_Q}}}
 		}%\]
 \end{mathpar}
-$\alpha_k'=\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k-1}}\!\!\Post''_{p}}}$\\
-$\forall l \in L_Q. v_l=v_{(n'_{k-1})l} \wedge v_l'=v_{(n'_k-1)l}$, \\
+$\alpha_k'=\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k-1}}\!\!\Post''_{j}}}$\\
+$\forall l \in L_Q. v_{kl}=v_{(n'_{k-1})l} \wedge v_{kl}'=v_{(n'_k-1)l}$\\
 $\displaystyle{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=\displaystyle{\mybigdotcup_{i=n'_{k-1}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k-1}}\!\!\!\Post''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k-1}}\!\!\!\Post''_{l}}}} \dotcup\\
@@
 
+Also note that for all $k\in[1..n-1]$, $v_{kl}'=v_{(k+1)l}$, and $v_{0l}=s_{0l}=s_l$ and $v'_{nl}=v_{(n_1+n_2+3) l}=u_{n_2 l} = s'_l$.
+
 %In this case, the number of weak open transitions
 %might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.\\
-Note that \[\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{p}}} = \alpha_k'\displaystyle{\subst{\bigotimes_{j=n'_{k-1}}^{0}\!\!\Post''_{p}}} = 
-\alpha_k'\displaystyle{\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{p}}}\]
-We now have: \TODO{add ref to eq 1 page above?}
-\[\Pred \implies \gamma_{j_0}=
-\vis{[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[1..n]]}\]
+Note that \[\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{j}}} =
+\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k-1}}\!\!\Post''_{j}\otimes\bigotimes_{j=n'_{k-1}-1}^{0}\!\!\Post''_{j}}} = \alpha_k'\displaystyle{\subst{\bigotimes_{j=n'_{k-1}-1}^{0}\!\!\Post''_{j}}} =
+\alpha_k'\displaystyle{\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}}\]
+We now have (the $\alpha'_p$ correspond to the observable $\alpha_k$ actions): \TODO{add ref to eq 1 page above?}
+\begin{eqnarray*}
+\Pred_\beta &\iff& \gamma_{j_0}=
+\vis{[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n_1+n_2+2]]}\\
+%&\iff& \gamma_{j_0}=
+%\vis{[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[1..n]]}\\
+&\iff& \gamma_{j_0}=
+[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[1..n]]
+\end{eqnarray*}
+
+We need now to show that this set of WOT verify the lemma.
 
@@
 \end{mathpar}
-We have by 	hypothesis: 	$s_{0l}=s_l$, $s_{(n+1)l}=s'_l$\\
-By considering $n=m_1+m_2+2$,  and $\forall p \in [0..n]$: \\
-$\Pred_{p}= \left\{
- \begin{array}{ll}
-\Pred_{1p} & \mbox{if }p<m_1\\
-\Pred_{2} & \mbox{if } p=m_1\\
-\Pred_{1(p-m_1)} & \mbox{if }p\geq m_1\\
-\end{array}
-\right. 
-\quad$
- $\qquad
-\Post_{p}= \left\{
- \begin{array}{ll}
-\Post_{1p} & \mbox{if }p<m_1\\
-\Post_{2} & \mbox{if } p=m_1\\
-\Post_{1(p-m_1)} & \mbox{if }p\geq m_1\\
-\end{array}
-\right. 
-$\\
-and similarly for $\beta_p$. Thus, we can rewrite $\gamma$ given in the hypothesis as: \\
-$\set{\gamma}= \displaystyle{\mybigdotcup_{p=0}^{n}
-\vis{\set{\beta_{p}}}\subst{\bigotimes_{p=n}^{0} \Post_{p}}}$\\
+
+%By considering $n=m_1+m_2+2$,  and $\forall p \in [0..n]$: \\
+%$\Pred_{p}= \left\{
+% \begin{array}{ll}
+%\Pred_{1p} & \mbox{if }p<m_1\\
+%\Pred_{2} & \mbox{if } p=m_1\\
+%\Pred_{1(p-m_1)} & \mbox{if }p\geq m_1\\
+%\end{array}
+%\right. 
+%\quad$
+% $\qquad
+%\Post_{p}= \left\{
+% \begin{array}{ll}
+%\Post_{1p} & \mbox{if }p<m_1\\
+%\Post_{2} & \mbox{if } p=m_1\\
+%\Post_{1(p-m_1)} & \mbox{if }p\geq m_1\\
+%\end{array}
+%\right. 
+%$\\
+%and similarly for $\beta_p$. Thus, we can rewrite $\gamma$ given in the hypothesis as: \\
+%$\set{\gamma}= \displaystyle{\mybigdotcup_{p=0}^{n}
+%\vis{\set{\beta_{p}}}\subst{\bigotimes_{p=n}^{0} \Post_{p}}}$\\
 Furthermore, still by hypothesis we have:\\

### 2019-07-09 2016-Weak-FH-Bisim/WeakBisim.tex
Tentatives sur lemma 6

@@
 		\text{and~~}  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) \qquad
- \text{and\qquad} \forall j\in J_p,\,\gamma_j= \mybigdotcup_{p=0}^n \gamma_{p j} \\
+ \text{and\qquad} \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n \gamma_{p j}^{j\in J_p} \\
  \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred = \Pred\,'
@@
 Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (are $\tau$ transition).
-By considering $\tau$  actions we split the sequence of actions into $n$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.
-We can decompose each of the $n$ subsequences; for $k\in [1..n]$ the position of the $k^{\text{th}}$ visible action is is $n_k$, $k\in [1..n-1]$ for  $n'_k$ is any index between $n_k$ and $n_{k+1}$,  $n'_0=0$ and $n'_n=n_1+n_2+3$.
-We obtain $n$ subsequences  made of the following OTs, for all $k\in [1..n]$ :\\
-$\forall p\! \in\! [n'_{k-1}..(n_k\!-\!1)] Q\models{\openrule
+By considering $\tau$  actions we split the sequence of actions into $n+1$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.
+We can decompose each of the $n+1$ subsequences; for $k\in [0..n]$ the position of the $k^{\text{th}}$ visible action is is $n_k$, $k\in [1..n-1]$ for  $n'_k$ is any index between $n_k$ and $n_{k+1}$,  $n'_0=0$ and $n'_{n+1}=n_1+n_2+3$.
+We obtain $n+1$ subsequences  made of the following OTs, for all $k\in [0..n]$ :\\
+$\forall p\! \in\! [n'_{k}..(n_k\!-\!1)] Q\models{\openrule
 			{
@@
 and
-$\forall p \in [(n_k\!+\!1)..(n_k'\!-\!1)]\,\, Q\models{\openrule
+$\forall p \in [(n_k\!+\!1)..(n'_{k+1}\!-\!1)]\,\, Q\models{\openrule
 			{
@@
 \end{mathpar}
-$\alpha_k'=\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k-1}}\!\!\Post''_{j}}}$\\
-$\forall l \in L_Q. v_{kl}=v_{(n'_{k-1})l} \wedge v_{kl}'=v_{(n'_k-1)l}$\\
-$\displaystyle{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=\displaystyle{\mybigdotcup_{i=n'_{k-1}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k-1}}\!\!\!\Post''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k-1}}\!\!\!\Post''_{l}}}} \dotcup\\
-~~\qquad \mybigdotcup_{i=n_k+1}^{n_k'-1}
-\vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}} \subst{\bigotimes_{l=i-1}^{n_k\!+\!1}\!\Post''_{l}\shortotimes\Post''_{n_k}\shortotimes\!\!\bigotimes_{l=n_k-1}^{n'_{k-1}}\!\!\!\Post''_{l}} }\\
-%
-\Pred_k=\bigwedge_{i=n'_{k-1}}^{n_k\!-\!1}\!\!\Pred''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k-1}}\!\!\Post_{j}}\land\Pred''_{n_k} \subst{\bigotimes_{j=n_k-1}^{n'_{k-1}}\!\!\Post''_{j}}\land\\ 
-~\qquad\quad\bigwedge_{i=n_k+1}^{n_k'-1}\!\!\!\Pred''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k-1}}\!\!\!\Post''_{j}\shortotimes\Post''_{n_k}\shortotimes\!\!\bigotimes_{j=n_k-1}^{n'_{k-1}}\!\!\!\Post''_{j}}
+$\alpha_k'=\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post''_{j}}}$\\
+$\forall l \in L_Q. v_{kl}=v_{(n'_{k})l} \wedge v_{kl}'=v_{(n'_k)l}$\\
+$\displaystyle{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=\displaystyle{\mybigdotcup_{i=n'_{k}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k}}\!\!\!\Post''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post''_{l}}}} \dotcup\\
+~~\qquad \mybigdotcup_{i=n_k+1}^{n'_{k+1}-1}
+\vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}} \subst{\bigotimes_{l=i-1}^{n_k\!+\!1}\!\Post''_{l}\shortotimes\Post''_{n_k}\shortotimes\!\!\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post''_{l}} }\\
+%
+\Pred_k=\bigwedge_{i=n'_{k}}^{n_k\!-\!1}\!\!\Pred''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\Post_{j}}\land\Pred''_{n_k} \subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post''_{j}}\land\\ 
+~\qquad\quad\bigwedge_{i=n_k+1}^{n'_{k+1}-1}\!\!\!\Pred''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\!\Post''_{j}\shortotimes\Post''_{n_k}\shortotimes\!\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post''_{j}}
 \\
-\Post_k= \bigotimes_{j=n_k'-1}^{n'_{k-1}}\!\!\Post''_{j}$\\
-
-Also note that for all $k\in[1..n-1]$, $v_{kl}'=v_{(k+1)l}$, and $v_{0l}=s_{0l}=s_l$ and $v'_{nl}=v_{(n_1+n_2+3) l}=u_{n_2 l} = s'_l$.
+\Post_k= \bigotimes_{j=n'_{k+1}-1}^{n'_{k}}\!\!\Post''_{j}$\\
+
+Also note that for all $k\in[0..n-1]$, $v_{kl}'=v_{(k+1)l}$, and $v_{0l}=s_{0l}=s_l$ and $v'_{nl}=v_{(n_1+n_2+3) l}=u_{n_2 l} = s'_l$.
 
@@
 Note that \[\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{j}}} =
-\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k-1}}\!\!\Post''_{j}\otimes\bigotimes_{j=n'_{k-1}-1}^{0}\!\!\Post''_{j}}} = \alpha_k'\displaystyle{\subst{\bigotimes_{j=n'_{k-1}-1}^{0}\!\!\Post''_{j}}} =
+\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post''_{j}\otimes\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j}}} = \alpha_k'\displaystyle{\subst{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j}}} =
 \alpha_k'\displaystyle{\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}}\]
@@
 
-We need now to show that this set of WOT verify the lemma.
+We need now to show that this set of WOT verify the conditions of the lemma, i.e. it is a set of WOT of the form:
+\[	Q\models{\openrule
+			{
+				\gamma_{p j}^{j\in J_p}, \Pred_p,  
+				\Post_p}
+			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
+				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
+		}\]
+With
+\[  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) \qquad\text{trivial}\]
+\[\text{and\qquad} \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n \gamma_{p j}^{j\in J_p}\]
+Indeed we have:
+\begin{equation*}
+\begin{split}
+\gamma_j^{j\in J}&=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!
+\Post_{1j}}}\dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }\\
+\end{split}\end{equation*}
+
+And thus, because $\beta_{pj}^{j\in J\cap \Holes(Q)}$ are equal to  $(\beta'_{1pj})^{j\in J\cap \Holes(Q)}$, $(\beta'_{2j})^{j\in J\cap \Holes(Q)}$, and $(\beta')_{3pj}^{j\in J\cap \Holes(Q)}$ (re-indexed), and additionally $(\beta')_{1pj}^{j\in J\cap \Holes(Q)}$, $(\beta')_{2j}^{j\in J\cap \Holes(Q)}$, and $(\beta')_{3pj}^{j\in J\cap \Holes(Q)}$ are identical to the holes labels $\beta_{1kj}^{j\in J\cap \Holes(Q)}$, $\beta_{2j}^{j\in J\cap \Holes(Q)}$, and $\beta_{3kj}^{j\in J\cap \Holes(Q)}$ when $Q$ moves\footnote{more precisely, when $Q$ moves either $\beta_{1kj}^{j\in J\cap \Holes(Q)}$ is not empty  and thus $(\beta')_{1pj}^{j\in J\cap \Holes(Q)}=\beta_{1kj}^{j\in J\cap \Holes(Q)}$, or both are empty if the holes perform no action}.
+We can assert a similar equality on postconditions, i.e.
+between $\Post''_p$ and $\Post''_{1k}$, $\Post''_{2}$, $\Post''_{3k}$ where $\Post''_{1p}$ is the restriction of $\Post_{1p}$ over variables of $\Leaves(Q)$ (see initial decomposition, case 1, 2, and 3 above).
+Overall, we have
+{\scriptsize \begin{equation*}
+\begin{split}
+\gamma_j^{j\in J\cap \Holes(Q)}&=\mybigdotcup_{i=0}^{m_1} \vis{\set{(\beta')_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!
+\Post''_{1j}}}\dotcup  \vis{\set{\beta'_2}\subst{\bigotimes_{j=m_1}^{0}\Post''_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}} }\\
+&=\mybigdotcup_{k=0}^n \left( \right)
+\end{split}\end{equation*}
+}
+% \text{and\qquad} \forall j\in J_p,\,\gamma_j= \mybigdotcup_{p=0}^n \gamma_{p j} \\
+% \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred = \Pred\,'
+%		\land \!\!\bigwedge_{p=0}^n((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} )
 

### 2019-07-10 2016-Weak-FH-Bisim/WeakBisim.tex
Skype version

@@
 				\Post}
-			{\ostate{s_l^{l\in L}} \OTWeakarrow {\alpha'}
+			{\ostate{s_l^{l\in L}} \OTWeakarrow {\alpha}
 				\ostate{s_l'^{\, l\in L}}} 
@@
            \set{\beta_2},\Pred_2,\Post_2 }
-         {\ostate{t_l^{l\in L}} \OTarrow {\alpha} \ostate{{t'}_l^{l\in L}}}
+         {\ostate{t_l^{l\in L}} \OTarrow {\alpha'} \ostate{{t'}_l^{l\in L}}}
 $ 
@@
 where\\
-$\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}}$\\
+$\alpha=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}}$\\
  for all $l\in L$: $s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
@@
            \beta_{2j}^{j\in J_2},\Pred_2,\Post_2 }
-         {\ostate{t} \OTarrow {\alpha} \ostate{t'}}$\\
+         {\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'} \ostate{(t'_l)^{l\in L_Q}}}$\\
 If $Q$ moves then we  obtain by Lemma \ref{lem-decompose}:\\
@@
 				{\Post'_2}}
-			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
+			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha'}
 				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
@@
 				{\Post'_2}}
-			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
-				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
+			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha'}
+				\ostate{(t_l)'^{\,l\in L\setminus L_Q}}}
 		}%\]
 	\,\text{~~and~~} \ostate{t_l^{l\in L_Q}} = 
-				\ostate{t_l'^{\,l\in L_Q}}$
+				\ostate{(t_l')^{\,l\in L_Q}}$
 
@@
 				\Post'}
-			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
+			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha''}
 				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
@@
 where:\\
-$\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}}$\\
+$\alpha''=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}}$
+We have:
+$\alpha''\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}}}=\alpha$
+as $\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}}}$ has no effect on variables of $P$ and thus on variables of $\alpha$, we have $\alpha=\alpha''$.
+\\
  for all $l\in L$: 
@@
 Concerning $Q$, we reduce the sequence of OTs to a path for which it moves in all steps.
-In other words, if there is $Q$ does not move at step $q$, then we have $\ostate{s_{q_l}^{l\in L_Q}} = \ostate{{s}_{(q+1) l}^{l\in L_Q}}$ , then we skip the state $\ostate{{s}_{(q+1) l}^{l\in L_Q}}$, i.e.
-we rename all the following states  $\ostate{s_{p l}^{l\in L_Q}}$ where $p\geq q+1$ by $\ostate{{s}_{(p-1) l}^{l\in L_Q}}$.
-Note that if $Q$ does an OT staying at the same state, we keep this necessary OT.
+In other words, if $Q$ does not move at step $q$, then we have $\ostate{s_{q_l}^{l\in L_Q}} = \ostate{{s}_{(q+1) l}^{l\in L_Q}}$ , then we skip the state $\ostate{{s}_{(q+1) l}^{l\in L_Q}}$, i.e.
+we rename all the following states  $\ostate{s_{p l}^{l\in L_Q}}$ where $p\geq q+1$ into $\ostate{{s}_{(p-1) l}^{l\in L_Q}}$.
+Note that self-loops where $Q$ does an action but stays at the same state are not removed.
 We proceed in the same way  for states named $u$.
@@
 $\\ 
-In this equation, and using case 1 above for all $k\in [0\ldots n_1]$ there is a $p\in [0..m_1]$ (following the re-indexing done in the removal of steps where $Q$ does not move) $\Pred_{1p}$ contains $ \alpha_{1p}=\beta_{1 p j_0}$ with $\alpha_{1p}=\alpha_k$.
+In this equation, and using case 1 above for all $k\in [0\ldots n_1]$ there is a $p\in [0..m_1]$ such that $\alpha_{1p}=\alpha_k$ (following the re-indexing done in the removal of steps where $Q$ does not move), we have $\Pred_{1p}$ contains $ \alpha_{1p}=\beta_{1 p j_0}$.
 Because $\beta_{1 p j_0}$ only contains variables of $P$ and $\alpha_k$ only variables of $Q$:
-\[(\alpha_{1p}=\beta_{1pj_0})\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\iff
- \beta_{1 p j_0}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}=\alpha_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post''_{j}}\]
+\begin{equation*}
+\begin{split}
+(\alpha_{1p}=\beta_{1pj_0})\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}&\iff
+\alpha_{1p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post''_{1j}}
+= \beta_{1 p j_0}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post'_{1j}} \\
+&\iff\alpha_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post''_{j}}= \beta_{1 p j_0}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post'_{1j}} 
+\end{split}
+\end{equation*}
 We have similar equations for $\alpha_{n_1+1}$ related with $\beta_{2 j_0}$ and the following $\alpha_k$ related with $\beta_{3 j_0}$ for some $p$.
@@
 &\iff& \gamma_{j_0}=
-[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[1..n]]
+[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n]]
 \end{eqnarray*}

### 2019-07-11 2016-Weak-FH-Bisim/WeakBisim.tex
yet another version of lemma 6
progress on proof of lemma 6
Proof of Lemma 6 -- convincing enough

@@
 \\
-		\text{and~~}  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) \qquad
- \text{and\qquad} \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n \gamma_{p j}^{j\in J_p} \\
- \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred = \Pred\,'
+		\text{and~\qquad}  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) 
+ \\
+\text{and\qquad }
+ \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigotimes_{i=p-1}^{0}\Post_i)} \\
+ \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\
+{\hspace{-3ex}}\text{and~~} \Pred \iff \Pred\,'
 		\land \!\!\bigwedge_{p=0}^n((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} )
@@
 %
-\Pred_k=\bigwedge_{i=n'_{k}}^{n_k\!-\!1}\!\!\Pred''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\Post_{j}}\land\Pred''_{n_k} \subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post''_{j}}\land\\ 
+\Pred_k=\bigwedge_{i=n'_{k}}^{n_k\!-\!1}\!\!\Pred''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\Post''_{j}}\land\Pred''_{n_k} \subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post''_{j}}\land\\ 
 ~\qquad\quad\bigwedge_{i=n_k+1}^{n'_{k+1}-1}\!\!\!\Pred''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\!\Post''_{j}\shortotimes\Post''_{n_k}\shortotimes\!\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post''_{j}}
@@
 \[  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) \qquad\text{trivial}\]
-\[\text{and\qquad} \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n \gamma_{p j}^{j\in J_p}\]
+\[ \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigotimes_{i=p-1}^{0}\Post_i)}\]
 Indeed we have:
@@
 \Post''_{1j}}}\dotcup  \vis{\set{\beta'_2}\subst{\bigotimes_{j=m_1}^{0}\Post''_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}} }\\
-&=\mybigdotcup_{k=0}^n \left( \right)
+&=\mybigdotcup_{k=0}^n \left( \mybigdotcup_{i=n'_k}^{n'_{k+1}-1}\beta_{ij}^{j\in J\cap \Holes(Q)}\subst{\bigotimes_{j=i-1}^{n'_k}\!\!\Post''_{j}\bigotimes_{j=n'_k-1}^{0}\!\!\Post''_{j}}\right)\\
+&=\mybigdotcup_{k=0}^n \left( \gamma_{kj}^{j\in J\cap \Holes(Q)}\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{k}}\right)
 \end{split}\end{equation*}
 }
-% \text{and\qquad} \forall j\in J_p,\,\gamma_j= \mybigdotcup_{p=0}^n \gamma_{p j} \\
-% \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred = \Pred\,'
-%		\land \!\!\bigwedge_{p=0}^n((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} )
-
-%$\displaystyle{\gamma_{j_0}}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta_{1i{j_0}}} \dotcup  \vis{{\beta_{2j_0}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3i{j_0}}}$. Additionally, we have
-%$[\alpha'_0.. \alpha'_n]$ is the list of non-$\tau$ $\alpha_p$.
-%% such that $p\in [0..(n_1\!+\!n_2\!+\!2)] \land \alpha_p\neq \tau$ where for all $k\in [0\ldots n_1+n_2+2]$, $\beta_{kj_0}=\alpha_k$. 
-%In other words, $\displaystyle{\mybigdotcup_{i=0}^{m_1}  \vis{\beta_{1i{j_0}}} \dotcup  \vis{{\beta_{2j_0}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3i{j_0}}} = [\alpha'_0..
-\alpha'_n]}$.
-%This ensures that $\gamma_{j_0}=[\alpha'_0..
-\alpha'_n]$.
-%
-%
-%Consequently
-
-%$\displaystyle{\gamma_{kj_0} }=\mybigdotcup_{i=0}^{(n'-1)}\!\!\vis{\beta^1_{ij_0}}\,\dotcup\,\vis{\set{\beta^2_{j_0}}}\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij_0}}$ \TODO{?????}\\
-
-\TODO{stopped here not sure about the following}
-
-Consequently, we have $n$ weak open transitions  $\symb{WOT}_k$ such that $k\in [1..n]$.
-Therefore, we can conclude that we have for all $k\in [1..n]$:  
-\begin{mathpar}
-Q\models{\openrule
-			{
-			\gamma_{kj}^{j\in J_k}, {\Pred_k}, {\Post_k}}
-			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
-				\ostate{s_{(p+1)l}^{l\in L_Q}}}
-		}%\]
-\end{mathpar}
-
-%By considering $n=m_1+m_2+2$,  and $\forall p \in [0..n]$: \\
-%$\Pred_{p}= \left\{
-% \begin{array}{ll}
-%\Pred_{1p} & \mbox{if }p<m_1\\
-%\Pred_{2} & \mbox{if } p=m_1\\
-%\Pred_{1(p-m_1)} & \mbox{if }p\geq m_1\\
-%\end{array}
-%\right. 
-%\quad$
-% $\qquad
-%\Post_{p}= \left\{
-% \begin{array}{ll}
-%\Post_{1p} & \mbox{if }p<m_1\\
-%\Post_{2} & \mbox{if } p=m_1\\
-%\Post_{1(p-m_1)} & \mbox{if }p\geq m_1\\
-%\end{array}
-%\right. 
+\[\forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i \text{see above}\]
+
+\[ \Pred = \Pred\,'
+		\land \!\!\bigwedge_{p=0}^n((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} )\]
+
+Indeed, \TODO{fill the empty lines (more complex but easy adaptation)}
+{\scriptsize \begin{equation*}
+\begin{split}
+\Pred&\iff\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\land
+\bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
+&\iff\bigwedge_{i=0}^{m_1}\left(\Pred'_{1p}
+		\land {\Pred''_{1p}}\land \alpha_{1p}=\beta_{1pj_0}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\right)\\
+&\qquad\land\\
+&\qquad\land\\
+&\iff\bigwedge_{i=0}^{m_1}\left((\Pred'_{1p}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}})
+		\land ({\Pred''_{1p}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post''_{1j}})\land (\alpha_{1p}=\beta_{1pj_0}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}})\right)\\
+&\qquad\land\\
+&\qquad\land\\
+&\iff \Pred'\land\bigwedge_{k=0}^n\Pred_k\bigotimes_{j=k-1}^{0}\!\!\Post_{j}\land\Pred_\beta
+\\&\iff \Pred'\land\bigwedge_{k=0}^n\Pred_k\bigotimes_{j=k-1}^{0}\!\!\Post_{j}\land
+(\gamma_{j_0}=[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n]])
+\end{split}\end{equation*}
+}
+Which is exactly what is needed.
+
+Finally we have
+\[\Post=\Post\,' \uplus \bigotimes_{p=n}^0
+		\Post_p  \]
+Because
+\begin{equation*}
+\begin{split}
+\Post&=\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}\\
+&=\bigotimes_{j=m_2}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}\\
+&\qquad \uplus \bigotimes_{j=m_2}^{0}\!\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}\\
+&=\Post' \uplus \bigotimes_{j=n'_{n+1}-1}^{0}\!\!\Post''_{j}
+\end{split}
+\end{equation*}
+%
+%Consequently, we have $n$ weak open transitions  $\symb{WOT}_k$ such that $k\in [1..n]$.
+%Therefore, we can conclude that we have for all $k\in [1..n]$:  
+%\begin{mathpar}
+%Q\models{\openrule
+%			{
+%			\gamma_{kj}^{j\in J_k}, {\Pred_k}, {\Post_k}}
+%			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
+%				\ostate{s_{(p+1)l}^{l\in L_Q}}}
+%		}%\]
+%\end{mathpar}
+%
+%%By considering $n=m_1+m_2+2$,  and $\forall p \in [0..n]$: \\
+%%$\Pred_{p}= \left\{
+%% \begin{array}{ll}
+%%\Pred_{1p} & \mbox{if }p<m_1\\
+%%\Pred_{2} & \mbox{if } p=m_1\\
+%%\Pred_{1(p-m_1)} & \mbox{if }p\geq m_1\\
+%%\end{array}
+%%\right. 
+%%\quad$
+%% $\qquad
+%%\Post_{p}= \left\{
+%% \begin{array}{ll}
+%%\Post_{1p} & \mbox{if }p<m_1\\
+%%\Post_{2} & \mbox{if } p=m_1\\
+%%\Post_{1(p-m_1)} & \mbox{if }p\geq m_1\\
+%%\end{array}
+%%\right. 
+%%$\\
+%%and similarly for $\beta_p$. Thus, we can rewrite $\gamma$ given in the hypothesis as: \\
+%%$\set{\gamma}= \displaystyle{\mybigdotcup_{p=0}^{n}
+%%\vis{\set{\beta_{p}}}\subst{\bigotimes_{p=n}^{0} \Post_{p}}}$\\
+%Furthermore, still by hypothesis we have:\\
+%$\Pred=\displaystyle{\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }\land \\
+%~\qquad \quad \bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}$\\
+%By replacing $\Pred_{1i}$,  $\Pred_2$, and $\Pred_{3i}$ by their equivalent formula obtained from cases 1, 2 and 3 we have:\\
+%$\Pred =\displaystyle{\bigwedge_{i=0}^{m_1}({\Pred'_{1i}}
+%		\land {\Pred''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}) \bigotimes_{j=i-1}^{0}\subst{\Post_{1j}}\land}\\
+%~~\qquad\qquad({\Pred'_2}\land {\Pred''_2}\land \alpha_2=\beta_{2j_0})	\bigotimes_{i=m_1}^{0}\subst{\Post_{1i}}\land\\
+%~~\qquad\qquad\bigwedge_{i=0}^{m_2} ({\Pred'_{3i}}\land {\Pred''_{3i}}\land \alpha_{3i}=\beta_{3ij_0})
+%\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}$\\
+%By distribution of the substitution operation over the logical operator we reformulate as:\\
+%$\Pred= \displaystyle{\big(\bigwedge_{i=0}^{m_1}
+%{\Pred'_{1i}}\bigotimes_{j=i-1}^{0}\subst{{\Post'_{1j}}}\big)
+%\land{\Pred'_2}\bigotimes_{i=m_1}^{0}\subst{{\Post'_{1i}}}\land} \\
+%~~\qquad\qquad\bigwedge_{i=0}^{m_2}{\Pred'_{3i}}\bigotimes_{j=i-1}^{0}\subst{{\Post'_{3j}}}\subst{{\Post'_2}}\bigotimes_{j=m_1}^{0}\subst{{\Post'_{1j}}} \land\\	
+%~\qquad\qquad\bigwedge_{i=0}^{m_1}({\Pred''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}) \bigotimes_{j=i-1}^{0}\subst{\Post_{1j}}\land({\Pred''_2}\land \alpha_2=\beta_{2j_0})	\bigotimes_{i=m_1}^{0}\subst{\Post_{1i}}\land\\
+%~\qquad\qquad\bigwedge_{i=0}^{m_2} ({\Pred''_{3i}}\land \alpha_{3i}=\beta_{3ij_0})\bigotimes_{j=i-1}^{0}\subst{\Post_{3j}}\subst{\Post_2}  \bigotimes_{i=m_1}^{0}\subst{\Post_{1i}}
 %$\\		
-%and similarly for $\beta_p$. Thus, we can rewrite $\gamma$ given in the hypothesis as: \\
-%$\set{\gamma}= \displaystyle{\mybigdotcup_{p=0}^{n}
-%\vis{\set{\beta_{p}}}\subst{\bigotimes_{p=n}^{0} \Post_{p}}}$\\
-Furthermore, still by hypothesis we have:\\
-$\Pred=\displaystyle{\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }\land \\
-~\qquad \quad \bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}$\\
-By replacing $\Pred_{1i}$,  $\Pred_2$, and $\Pred_{3i}$ by their equivalent formula obtained from cases 1, 2 and 3 we have:\\
-$\Pred =\displaystyle{\bigwedge_{i=0}^{m_1}({\Pred'_{1i}}
-		\land {\Pred''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}) \bigotimes_{j=i-1}^{0}\subst{\Post_{1j}}\land}\\
-~~\qquad\qquad({\Pred'_2}\land {\Pred''_2}\land \alpha_2=\beta_{2j_0})	\bigotimes_{i=m_1}^{0}\subst{\Post_{1i}}\land\\
-~~\qquad\qquad\bigwedge_{i=0}^{m_2} ({\Pred'_{3i}}\land {\Pred''_{3i}}\land \alpha_{3i}=\beta_{3ij_0})
-\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}$\\
-By distribution of the substitution operation over the logical operator we reformulate as:\\
-$\Pred= \displaystyle{\big(\bigwedge_{i=0}^{m_1}
-{\Pred'_{1i}}\bigotimes_{j=i-1}^{0}\subst{{\Post'_{1j}}}\big)
-\land{\Pred'_2}\bigotimes_{i=m_1}^{0}\subst{{\Post'_{1i}}}\land} \\
-~~\qquad\qquad\bigwedge_{i=0}^{m_2}{\Pred'_{3i}}\bigotimes_{j=i-1}^{0}\subst{{\Post'_{3j}}}\subst{{\Post'_2}}\bigotimes_{j=m_1}^{0}\subst{{\Post'_{1j}}} \land\\	
-~\qquad\qquad\bigwedge_{i=0}^{m_1}({\Pred''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}) \bigotimes_{j=i-1}^{0}\subst{\Post_{1j}}\land({\Pred''_2}\land \alpha_2=\beta_{2j_0})	\bigotimes_{i=m_1}^{0}\subst{\Post_{1i}}\land\\
-~\qquad\qquad\bigwedge_{i=0}^{m_2} ({\Pred''_{3i}}\land \alpha_{3i}=\beta_{3ij_0})\bigotimes_{j=i-1}^{0}\subst{\Post_{3j}}\subst{\Post_2}  \bigotimes_{i=m_1}^{0}\subst{\Post_{1i}}
-$\\		
-Thus, we can write the formula as follows:\\
-$\Pred= \Pred\,' \wedge \displaystyle{\bigwedge_{p=0}^{n}}((\alpha_p= \beta_{pj_0}\land \Pred_p)\bigotimes_{i=p-1}^{0}\Post_i)$\\
-We proceed the same way with the postcondition,  we have:\\
-$\Post=\displaystyle{\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}$\\
-By replacing ${\Post_{1i}}$,  $\Post_2$, and ${\Post_{3i}}$ their values obtained from the cases 1, 2, and 3, and because the ${\Post'_i}$ and ${\Post''_i}$ are independent (the ${\Post'_i}$ concern the leaves of $P$ while the ${\Post''_i}$ concern the leaves of $Q$), we obtain:\\
-$\Post= \displaystyle{\bigotimes_{i=m_2}^{0}\subst{{\Post'_{3i}}\uplus 
-		{\Post''_{3i}}} \subst{{\Post'_2}\uplus 
-		{\Post''_2}} \bigotimes_{j=m_1}^{0}\subst{ {\Post'_{1i}}\uplus 
-		{\Post''_{1i}}}}\\
-~~\qquad= \bigotimes_{i=m_2}^{0}{\Post'_{3i}}\subst{{\Post'_2}}\bigotimes_{j=m_1}^{0}\subst{{\Post'_{1j}}} \uplus \bigotimes_{i=m_2}^{0}{\Post''_{3i}}\subst{{\Post''_2}}\bigotimes_{j=m_1}^{0}\subst{{\Post''_{1j}}} \\
-~~\qquad= \Post' \uplus \bigotimes_{j=n}^{0} \Post_j $\\
+%Thus, we can write the formula as follows:\\
+%$\Pred= \Pred\,' \wedge \displaystyle{\bigwedge_{p=0}^{n}}((\alpha_p= \beta_{pj_0}\land \Pred_p)\bigotimes_{i=p-1}^{0}\Post_i)$\\
+%We proceed the same way with the postcondition,  we have:\\
+%$\Post=\displaystyle{\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}$\\
+%By replacing ${\Post_{1i}}$,  $\Post_2$, and ${\Post_{3i}}$ their values obtained from the cases 1, 2, and 3, and because the ${\Post'_i}$ and ${\Post''_i}$ are independent (the ${\Post'_i}$ concern the leaves of $P$ while the ${\Post''_i}$ concern the leaves of $Q$), we obtain:\\
+%$\Post= \displaystyle{\bigotimes_{i=m_2}^{0}\subst{{\Post'_{3i}}\uplus 
+%		{\Post''_{3i}}} \subst{{\Post'_2}\uplus 
+%		{\Post''_2}} \bigotimes_{j=m_1}^{0}\subst{ {\Post'_{1i}}\uplus 
+%		{\Post''_{1i}}}}\\
+%~~\qquad= \bigotimes_{i=m_2}^{0}{\Post'_{3i}}\subst{{\Post'_2}}\bigotimes_{j=m_1}^{0}\subst{{\Post'_{1j}}} \uplus \bigotimes_{i=m_2}^{0}{\Post''_{3i}}\subst{{\Post''_2}}\bigotimes_{j=m_1}^{0}\subst{{\Post''_{1j}}} \\
+%~~\qquad= \Post' \uplus \bigotimes_{j=n}^{0} \Post_j $\\
 \qed

### 2019-07-11 2016-Weak-FH-Bisim/WeakBisim.tex
notation lemma7

@@
 \[\forall h\!\in\![0..k].Q\models\openrule
-    {\set{\beta^1_h},\Pred^1_h,\Post^1_h   }
-         {\ostate{{(s^1_{h})}} \OTarrow {\tau} \ostate{{(s^1_{(h+1)})}}}
+    {\set{\beta_{1h}},\Pred_{1h},\Post_{1h}   }
+         {\ostate{{(s_{1h})}} \OTarrow {\tau} \ostate{{(s_{1(h+1)})}}}
 \]
@@
 	{
-		\set{\beta^2},
-		 \Pred^2,  
-		\Post^2}
-	{\ostate{s^2_{0}}\OTarrow {\alpha_Q}
-		\ostate{s^2_{1}}}
+		\set{\beta_2},
+		 \Pred_2,  
+		\Post_2}
+	{\ostate{s_{20}}\OTarrow {\alpha_Q}
+		\ostate{s_{21}}}
 }
@@
          {
-           \set{\beta^3_h},\Pred^3_h, \Post^3_h}
-         { \ostate{(s^3_h)} \OTarrow {\tau} \ostate{(s^3_{(h+1)})}} \]
+           \set{\beta_{3h}},\Pred_{3h}, \Post_{3h}}
+         { \ostate{(s_{3h})} \OTarrow {\tau} \ostate{(s_{3(h+1)})}} \]
 
 such that 
-$s_i^{i\in L_Q}=s^1_{0} \wedge s^1_{(k+1) i}=s^2_{0} \wedge  s^2_{1}= s^3_{0} \wedge s^3_{(k'+1) i}={s'}_i^{i\in L_Q}$\\
-
-$\displaystyle{\set{\gamma}=\mybigdotcup_{h=0}^{k} \vis{\set{\beta^1_h}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{h=0}^{k'} \vis{\set{\beta^3_h}}}
+$s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\
+
+$\displaystyle{\set{\gamma}=\mybigdotcup_{h=0}^{k} \vis{\set{\beta_{1h}}} \dotcup  \vis{\set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}}}}
 \\
-\Pred_Q=\bigwedge_{h=0}^{k}\!\big(\Pred^1_h\bigotimes_{j=h-1}^{0}\subst{\Post_j^1}\big)\land \Pred^2\bigotimes_{h=k}^{0}\subst{\Post_h^1}\land\\~\qquad\qquad \bigwedge_{h=0}^{k'}\!\Pred_h^3\big(\bigotimes_{j=h-1}^{0}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{h=k}^{0}\subst{\Post_h^1}\big)
+\Pred_Q=\bigwedge_{h=0}^{k}\!\big(\Pred_{1h}\bigotimes_{j=h-1}^{0}\subst{\Post_j^1}\big)\land \Pred_2\bigotimes_{h=k}^{0}\subst{\Post_{1h}}\land\\~\qquad\qquad \bigwedge_{h=0}^{k'}\!\Pred_{3h}\big(\bigotimes_{j=h-1}^{0}\subst{\Post_{3j}}\subst{\Post_2}  \bigotimes_{h=k}^{0}\subst{\Post_{1h}}\big)
 \\
-\Post_Q=\bigotimes_{h=k'}^{0}\Post^3_h\subst{\Post^2}\bigotimes_{j=k}^{0}\subst{\Post^1_j}
+\Post_Q=\bigotimes_{h=k'}^{0}\Post_{3h}\subst{\Post_2}\bigotimes_{j=k}^{0}\subst{\Post_{1j}}
 $
@@
     {
-       \set{\beta^1_h},{\Pred^1_h},{\Post^1_h}   }
-         {\ostate{s^1_h\uplus s^{i\in L}_{i} } \OTarrow {\tau} \ostate{s^1_{h+1}\uplus s^{i\in L}_{i}}}\]
+       \set{\beta_{1h}},{\Pred_{1h}},{\Post_{1h}}   }
+         {\ostate{s_{1h}\uplus s^{i\in L}_{i} } \OTarrow {\tau} \ostate{s_{1(h+1)}\uplus s^{i\in L}_{i}}}\]
 
@@
 			{\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}, 
-			\Pred\land\Pred^2\land \alpha_Q=\beta_{j_0 },  
-			\Post\uplus \Post^2}
-{\ostate{s^{i\in L}_{i}\uplus s_0^2} \OTarrow {\alpha} \ostate{{s'}^{i\in L}_{i}\uplus s_1^2}}
+			\Pred\land\Pred_2\land \alpha_Q=\beta_{j_0 },  
+			\Post\uplus \Post_2}
+{\ostate{s^{i\in L}_{i}\uplus s_{20}} \OTarrow {\alpha} \ostate{{s'}^{i\in L}_{i}\uplus s_{21}}}
 	}
@@
 \Post_c}
-         {\ostate{s^1_0\uplus s^{i\in L}_{i}} \OTWeakarrow {\alpha} 
-	\ostate{{{s'}^{i\in L}_{i}\uplus s_{k'+1}^3}}}\] 
+         {\ostate{s_{10}\uplus s^{i\in L}_{i}} \OTWeakarrow {\alpha} 
+	\ostate{{{s'}^{i\in L}_{i}\uplus s_{3(k'+1)}}}}\] 
 where
-\[\set{\gamma'}=\mybigdotcup_{h=0}^k\vis{\set{\beta^1_h}} \dotcup \vis{{\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'}\vis{\set{\beta^3_h}}\]
+\[\set{\gamma'}=\mybigdotcup_{h=0}^k\vis{\set{\beta_{1h}}} \dotcup \vis{{\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'}\vis{\set{\beta_{3h}}}\]
 \[
-\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred^1_h}\subst{\bigotimes_{i=h-1}^{0}\Post_i^1}\land
-\left(Pred\land\Pred^2\land \alpha_Q=\beta_{j_0 }\right)\subst{\bigotimes_{i=k}^{0}{\Post_i^1}}\land\\\displaystyle
-\bigwedge_{h=0}^{k'}{\Pred^3_h}\subst{\bigotimes_{i=h-1}^{0}{\Post_i^3}\shortotimes({\Post\uplus \Post^2})\shortotimes\bigotimes_{i=k}^{0}{\Post_i^1}}
+\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_i^1}\land
+\left(Pred\land\Pred_2\land \alpha_Q=\beta_{j_0 }\right)\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land\\\displaystyle
+\bigwedge_{h=0}^{k'}{\Pred_{3h}}\subst{\bigotimes_{i=h-1}^{0}{\Post_{3i}}\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}
 \end{array}
@@
 
-\[\Post_c=(\bigotimes_{i=k'}^{0}{\Post_i^3})\shortotimes({\Post\uplus \Post^2})\shortotimes\bigotimes_{i=k}^{0}{\Post_i^1}
+\[\Post_c=(\bigotimes_{i=k'}^{0}{\Post_{3i}})\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}
 \]
-Note that we have $s_i^{i\in L_Q}=s^1_{0} \wedge s^1_{(k+1) i}=s^2_{0} \wedge  s^2_{1}= s^3_{0} \wedge s^3_{(k'+1) i}={s'}_i^{i\in L_Q}$\\
-
-Note also that $\Post$ only acts on variables of $P$ while $\Post^1_i$ only acts on state variables of $Q$. A
+Note that we have $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\
+
+Note also that $\Post$ only acts on variables of $P$ while $\Post_{1i}$ only acts on state variables of $Q$. A
 \end{proof}
@@
 $\forall p\!\in\![0..m_1].P\models\openrule
-    {\set{\beta^1_p},\Pred^1_p,\Post^1_p   }
-         {\ostate{{(s^1_{pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s^1_{(p+1)i})}^{i\in L}}} \wedge
+    {\set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
+         {\ostate{{(s_{1pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s_{1(p+1)i})}^{i\in L}}} \wedge
 P\models\openrule
-         {\set{\beta^2},\Pred^2,\Post^2 }
-         {\ostate{({s_{0i}^2})^{i\in L}} \OTarrow {\alpha} \ostate{({s_{1i}^2})^{i\in L}}}
+         {\set{\beta_2},\Pred_2,\Post_2 }
+         {\ostate{({s_{20i}})^{i\in L}} \OTarrow {\alpha} \ostate{({s_{21i}})^{i\in L}}}
 \wedge\\
@@
          {
-           \set{\beta^3_p},\Pred^3_p, \Post^3_p}
-         { \ostate{(s^3_{pi})^{i\in L}} \OTarrow {\tau} \ostate{(s^3_{(p+1)i})^{i\in L}}}$ 
+           \set{\beta_{3p}},\Pred_{3p}, \Post_{3p}}
+         { \ostate{(s_{3pi})^{i\in L}} \OTarrow {\tau} \ostate{(s_{3(p+1)i})^{i\in L}}}$ 
 \\
 where for all $i\in L$:\\
-$s_i=s^1_{0 i} \wedge s^1_{(m_1+1) i}=s^2_{0i} \wedge  s^2_{1i}= s^3_{0 i} \wedge s^3_{(m_2+1) i}=s'_i$\\
-
-$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{p=0}^{m_1} \vis{\set{\beta^1_p}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{p=0}^{m_2} \vis{\set{\beta^3_p}}}\\
-\Pred=\bigwedge_{p=0}^{m_1}\!\big(\Pred^1_p\bigotimes_{j=p-1}^{0}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{p=m_1}^{0}\subst{\Post_p^1}\land \bigwedge_{p=0}^{m_2}\!\Pred_p^3\big(\!\!\bigotimes_{j=p-1}^{0}\subst{\Post^3_j}\subst{\Post^2}\!\!
-\bigotimes_{p=m_1}^{0}\subst{\Post_p^1}\big)\\
-\Post=\bigotimes_{p=m_2}^{0}\Post^3_p\subst{\Post^2}\bigotimes_{j=m_1}^{0}\subst{\Post^1_j}
+$s_i=s_{10 i} \wedge s_{1(m_1+1) i}=s_{20i} \wedge  s_{21i}= s_{30 i} \wedge s_{3(m_2+1) i}=s'_i$\\
+
+$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{p=0}^{m_1} \vis{\set{\beta_{1p}}} \dotcup  \vis{\set{\beta_2}} \dotcup \mybigdotcup_{p=0}^{m_2} \vis{\set{\beta_{3p}}}}\\
+\Pred=\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\bigotimes_{j=p-1}^{0}\subst{\Post_{1j}}\big)\land\Pred^2\bigotimes_{p=m_1}^{0}\subst{\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\big(\!\!\bigotimes_{j=p-1}^{0}\subst{\Post_{3j}}\subst{\Post_2}\!\!
+\bigotimes_{p=m_1}^{0}\subst{\Post_{1p}}\big)\\
+\Post=\bigotimes_{p=m_2}^{0}\Post_{3p}\subst{\Post_2}\bigotimes_{j=m_1}^{0}\subst{\Post_{1j}}
 $\\

### 2019-07-12 2016-Weak-FH-Bisim/WeakBisim.tex
skype call

@@
 $\alpha''=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}}$
+
 We have:
-$\alpha''\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}}}=\alpha$
-as $\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}}}$ has no effect on variables of $P$ and thus on variables of $\alpha$, we have $\alpha=\alpha''$.
+$\alpha=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}}\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}}}=\alpha''\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}}}$.\\
+As $\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}}}$ has no effect on variables of $P$ and thus on variables of $\alpha$, we have $\alpha=\alpha''$.
 \\
@@
 \end{equation*}
-We have similar equations for $\alpha_{n_1+1}$ related with $\beta_{2 j_0}$ and the following $\alpha_k$ related with $\beta_{3 j_0}$ for some $p$.
+We can optain similar equations for $\alpha_{n_1+1}$ related with $\beta_{2 j_0}$ and the  $\alpha_k$ for $k\geq n_1+2$ related with $\beta_{3 p j_0}$ for some $p$.
 Note that the substitutions are however more complex.
@@
 By considering $\tau$  actions we split the sequence of actions into $n+1$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.
-We can decompose each of the $n+1$ subsequences; for $k\in [0..n]$ the position of the $k^{\text{th}}$ visible action is is $n_k$, $k\in [1..n-1]$ for  $n'_k$ is any index between $n_k$ and $n_{k+1}$,  $n'_0=0$ and $n'_{n+1}=n_1+n_2+3$.
+We can decompose each of the $n+1$ subsequences; for $k\in [0..n]$ the position of the $k^{\text{th}}$ visible action is  $n_k$, for $k\in [1..n]$,  $n'_k$ is any index between $n_{k-1}$ and $n_k$, additionally $n'_0=0$ and $n'_{n+1}=n_1+n_2+3$.
 We obtain $n+1$ subsequences  made of the following OTs, for all $k\in [0..n]$ :\\
@@
 \Pred_\beta &\iff& \gamma_{j_0}=
-\vis{[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n_1+n_2+2]]}\\
+\mybigdotcup_{p=0}^{p=n_1+n_2+2}
+\vis{\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}}\\
+%&\iff&\gamma_{j_0}=
+%\mybigdotcup_{p=0}^{p=n_1+n_2+2}
+%\vis{\alpha_{p}\subst{\bigotimes_{j=p-1}^{n'_p}\!\!\Post_{j}}\subst{\bigotimes_{j=n'_p-1}^{0}\!\!\Post_{j}}}\\
+%\vis{[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n_1+n_2+2]]}\\
 %&\iff& \gamma_{j_0}=

### 2019-07-12 2016-Weak-FH-Bisim/WeakBisim.tex
in proof of lemma 7
proof of lemma 7 OK

@@
 \usepackage{DotArrow}
+\usepackage{hyperref}
 
@@
 $
-\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n}^{0}\Post_j^1}}\\
+\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n}^{0}\Post_{1j}}}\\
 s=s_{10} \wedge s_{1(n+1)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
@@
 		\Post_2}
-	{\ostate{s_{20}}\OTarrow {\alpha_Q}
+	{\ostate{s_{20}}\OTarrow {\alpha'_Q}
 		\ostate{s_{21}}}
@@
 such that 
+$\alpha_Q=\alpha'_Q\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$\\
 $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\
@@
 \Post_c}
-         {\ostate{s_{10}\uplus s^{i\in L}_{i}} \OTWeakarrow {\alpha} 
+         {\ostate{s_{10}\uplus s^{i\in L}_{i}} \OTWeakarrow {\alpha'} 
 	\ostate{{{s'}^{i\in L}_{i}\uplus s_{3(k'+1)}}}}\] 
 where
-\[\set{\gamma'}=\mybigdotcup_{h=0}^k\vis{\set{\beta_{1h}}} \dotcup \vis{{\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'}\vis{\set{\beta_{3h}}}\]
+\[\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}} \]
+and $\alpha=\alpha'$  because $\Post_{1j}$ acts on variables of $Q$ and $\alpha$ contains only variables of $P$
+
+\[\set{\gamma'}=\mybigdotcup_{h=0}^k\vis{\set{\beta_{1h}}} \dotcup \vis{{\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'}\vis{\set{\beta_{3h}}}=\set{\gamma}\uplus\vis{\beta_j^{j\in J\setminus \{j_0\}}}\]
 \[
-\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_i^1}\land
-\left(Pred\land\Pred_2\land \alpha_Q=\beta_{j_0 }\right)\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land\\\displaystyle
+\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_i{1i}}\land
+\left(Pred\land\Pred_2\land \alpha'_Q=\beta_{j_0 }\right)\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land\\\displaystyle
 \bigwedge_{h=0}^{k'}{\Pred_{3h}}\subst{\bigotimes_{i=h-1}^{0}{\Post_{3i}}\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}
@@
 
-Note also that $\Post$ only acts on variables of $P$ while $\Post_{1i}$ only acts on state variables of $Q$. A
+Note also that $\Post$ only acts on variables of $P$ while $\Post_{1i}$ only acts on state variables of $Q$.
+We conclude on predicate and posts as follows\footnote{$\Post_{1i}$ only has an effect on variables of $Q$ and thus does not modify $\Pred$ or $\beta_{j_0}$}:
+\begin{equation*}
+\begin{split}
+\Pred_c&=\Pred_Q\land\Pred\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land
+(\alpha'_Q=\beta_{j_0})subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\\
+&=\Pred_Q\land\Pred\land \alpha_Q=\beta_{j_0}
+\end{split}
+\end{equation*}
+\begin{equation*}
+\begin{split}
+\Post_c&=\Post\uplus\Post_Q
+\end{split}
+\end{equation*}
+\qed
 \end{proof}

### 2019-07-15 2016-Weak-FH-Bisim/WeakBisim.tex
working on lemma 8 (minor progress)

@@
 \end{mathpar}
+\TODO{add posts to gammaj's above}
 Then, we have\\[-2ex]
@@
 \end{lemma}
-\TODO{Proof starts from here}
 
@@
          {\set{\beta_2},\Pred_2,\Post_2 }
-         {\ostate{({s_{20i}})^{i\in L}} \OTarrow {\alpha} \ostate{({s_{21i}})^{i\in L}}}
+         {\ostate{({s_{20i}})^{i\in L}} \OTarrow {\alpha'} \ostate{({s_{21i}})^{i\in L}}}
 \wedge\\
@@
 $s_i=s_{10 i} \wedge s_{1(m_1+1) i}=s_{20i} \wedge  s_{21i}= s_{30 i} \wedge s_{3(m_2+1) i}=s'_i$\\
-
-$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{p=0}^{m_1} \vis{\set{\beta_{1p}}} \dotcup  \vis{\set{\beta_2}} \dotcup \mybigdotcup_{p=0}^{m_2} \vis{\set{\beta_{3p}}}}\\
-\Pred=\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\bigotimes_{j=p-1}^{0}\subst{\Post_{1j}}\big)\land\Pred^2\bigotimes_{p=m_1}^{0}\subst{\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\big(\!\!\bigotimes_{j=p-1}^{0}\subst{\Post_{3j}}\subst{\Post_2}\!\!
-\bigotimes_{p=m_1}^{0}\subst{\Post_{1p}}\big)\\
-\Post=\bigotimes_{p=m_2}^{0}\Post_{3p}\subst{\Post_2}\bigotimes_{j=m_1}^{0}\subst{\Post_{1j}}
-$\\
-
-Note that, for $l\in\{1,2,3\}$ if $(\beta^l_p)_{j_0}=\tau$ because of Definition \ref{def:Non-ObsTau}, $P$ necessarily makes a $\tau$ open transition and remains in the same state, ($s_p = s_{p+1}$).
+\[\alpha=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}}\]
+\[\displaystyle{
+\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\Post_{1j}}}}\]
+\begin{equation*}
+\begin{split}
+\Pred&g=\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\bigotimes_{j=p-1}^{0}\subst{\Post_{1j}}\big)\land\Pred^2\bigotimes_{p=m_1}^{0}\subst{\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\big(\!\!\bigotimes_{j=p-1}^{0}\subst{\Post_{3j}}\subst{\Post_2}\!\!
+\bigotimes_{p=m_1}^{0}\subst{\Post_{1p}}\big)
+\\
+\Post&=\bigotimes_{p=m_2}^{0}\Post_{3p}\subst{\Post_2}\bigotimes_{j=m_1}^{0}\subst{\Post_{1j}}
+\end{split}
+\end{equation*}
+
+Note that, for $l\in\{1,2,3\}$ if $\beta^l_{p j_0}=\tau$, then, because of Definition \ref{def:Non-ObsTau}, $P$ necessarily makes a $\tau$ open transition and remains in the same state, ($s_p = s_{p+1}$).
 Thus without loss of generality, we can bypass such an open transition and obtain another decomposition of the WOT without the open transition that requires ${\beta^l_{p{j_0}}}=\tau$.

### 2019-07-15 2016-Weak-FH-Bisim/WeakBisim.tex
premier dessins SimpleProt

--- 2019-07-12 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 by any correct instantiation of the holes.
-As a consequence, our model allows us to reason on composition operators as well as on full-size distributed systems.
-The parametric nature of the model and the properties of compositionability of the equivalence relations thus play a major role here and are the main strengths of  our contribution.
+As a consequence, our model allows us to reason on composition
+operators as well as on full-size distributed systems. The parametric
+nature of the model and the properties of compositionability of the
+equivalence relations thus play a major role here and are the main
+strengths of  our contribution.
 
@@
 \paragraph{Structure}
-This article is organised as follows.
-Section~\ref{sec:notations} provides the definition of pNets and introduces the notations used in this paper.
-Section~\ref{sec:OT} defines open automata, i.e.
-automata with parameters and transitions conditioned by the behaviour of ``holes''; a strong bisimulation equivalence for open automata is also presented in this section.
-Section~\ref{section:op-semantics} gives the semantics of open pNets expressed as weak automata, and states compositional properties on the strong bisimulation for open pNets.
-Finally, Section~\ref{sec:weak} defines a weak bisimulation equivalence on open automata and derives weak bisimilarity for pNets, together with properties on compositionality of weak bisimulaiton for open pNets.
-Finally, Section~\ref{section:conclusion} concludes the paper.
+This article is organised as follows. Section~\ref{sec:notations}
+provides the definition of pNets and introduces the notations used in
+this paper. Section~\ref{sec:OT} defines open automata, i.e. automata
+with parameters and transitions conditioned by the behaviour of
+``holes''; a strong bisimulation equivalence for open automata is also
+presented in this section. Section~\ref{section:op-semantics} gives
+the semantics of open pNets expressed as weak automata, and states
+compositional properties on the strong bisimulation for open
+pNets. Finally, Section~\ref{sec:weak} defines a weak bisimulation
+equivalence on open automata and derives weak bisimilarity for pNets,
+together with properties on compositionality of weak bisimulaiton for
+open pNets. Finally, Section~\ref{section:conclusion} concludes the
+paper.
 
@@
   \centerline{
-   \includegraphics[width=8cm]{XFIG/ABP-Schema}
-   }
-   \caption{Schema of the ABP example}  \label{ABP:Schema}
+   \includegraphics[width=8cm]{XFIG/SimpleProt-Schema}
+   }
+   \caption{Schema of the Simple Protocol Example}  \label{SimpleProt:Schema}
 \end{figure}
@@
 
-  \centerline{
-   \includegraphics[width=3.5cm]{XFIG/PerfectMedium}
-   \hspace{0.5cm}
-   \includegraphics[width=4cm]{XFIG/FaultyMedium}
-   }
-   \caption{Perfect and faulty (loosing and duplicating) media}  \label{schema:ABP-media}
+  %% \centerline{
+  %%  \includegraphics[width=3.5cm]{XFIG/PerfectMedium}
+  %%  \hspace{0.5cm}
+  %%  \includegraphics[width=4cm]{XFIG/FaultyMedium}
+  %%  }
+  %%  \caption{Perfect and faulty (loosing and duplicating) media}  \label{schema:ABP-media}
 
   %\end{minipage}
-  \vspace{1cm}
+%  \vspace{1cm}
 %\begin{minipage}{6cm}
-  \centerline{\includegraphics[width=11cm]{XFIG/ABP4-Schema}}
-  \caption{Composed pNet with the ABP protocol}  \label{schema:ABP-composed}
+  \centerline{\includegraphics[width=11cm]{XFIG/SimpleProt-pNet}}
+  \caption{Composed pNet with the Simple Protocol}  \label{schema:SimpleProt-composed}
 %\end{minipage}
@@
 
-Fig. \ref{ABP:Schema} shows the example principle: two unspecified
+Fig. \ref{SimpleProt:Schema} shows the example principle: two unspecified
 processes $P$ and $Q$ (Holes) communicate messages, with a data value
@@
 
+\section{ABP}
+I have collected here all previous items about ABP, in case we wnat to
+reuse them later
+
+\begin{figure}[t]
+  \centerline{
+   \includegraphics[width=8cm]{XFIG/ABP-Schema}
+   }
+   \caption{Schema of the ABP example}  \label{ABP:Schema}
+\end{figure}
+
 \section{Discussion on substitution, matching, unification}

### 2019-07-16 2016-Weak-FH-Bisim/WeakBisim.tex
Work on lemma 8

@@
 
-\begin{lemma}[Weak open transition composition]\label{lem-Weakcompose} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
+\begin{lemma}[Weak open transition composition]\label{lem-Weakcompose1} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
 	Suppose $j_0\in J$  and additionally:\\[-2ex]
@@
 	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
-		\ostate{s_i'^{\, i\in L}}}
+		\ostate{(s_i')^{\, i\in L}}}
 }\\
@@
 	{\ostate{s_{i}^{i\in L_Q}} \OTWeakarrow {\alpha_Q}
-		\ostate{{s'}_{i}^{\, i\in L_Q}}}
+		\ostate{(s'_{i})^{\, i\in L_Q}}}
 }%\]
@@
 		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
-			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
+			\ostate{(s_i')^{\, i\in L\uplus L_Q}}}
 	}
@@
 		\Post_t
+\\
+\forall{i\in L_Q}.\,s_i=s_{0i} \text{\quad and \quad} \forall {i\in L_Q}.\,s'_i=s_{(n+1) i}
 \end{mathpar}
@@
 $\forall p\!\in\![0..m_1].P\models\openrule
-    {\set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
+    {{\beta_{1pj}^{j\in J_{1p}}},\Pred_{1p},\Post_{1p}   }
          {\ostate{{(s_{1pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s_{1(p+1)i})}^{i\in L}}} \wedge
 P\models\openrule
-         {\set{\beta_2},\Pred_2,\Post_2 }
+         {\beta_2^{j\in J_2},\Pred_2,\Post_2 }
          {\ostate{({s_{20i}})^{i\in L}} \OTarrow {\alpha'} \ostate{({s_{21i}})^{i\in L}}}
@@
          {
-           \set{\beta_{3p}},\Pred_{3p}, \Post_{3p}}
+           \beta_{3pj}^{j\in J_{3p}},\Pred_{3p}, \Post_{3p}}
          { \ostate{(s_{3pi})^{i\in L}} \OTarrow {\tau} \ostate{(s_{3(p+1)i})^{i\in L}}}$ 
@@
 \[\displaystyle{
-\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\Post_{1j}}}}\]
+\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{1p}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\Post_{1j}}}}\]
 \begin{equation*}
 \begin{split}
-\Pred&g=\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\bigotimes_{j=p-1}^{0}\subst{\Post_{1j}}\big)\land\Pred^2\bigotimes_{p=m_1}^{0}\subst{\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\big(\!\!\bigotimes_{j=p-1}^{0}\subst{\Post_{3j}}\subst{\Post_2}\!\!
+\Pred&=\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\bigotimes_{j=p-1}^{0}\subst{\Post_{1j}}\big)\land\Pred^2\bigotimes_{p=m_1}^{0}\subst{\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\big(\!\!\bigotimes_{j=p-1}^{0}\subst{\Post_{3j}}\subst{\Post_2}\!\!
 \bigotimes_{p=m_1}^{0}\subst{\Post_{1p}}\big)
@@
 
-Note that, for $l\in\{1,2,3\}$ if $\beta^l_{p j_0}=\tau$, then, because of Definition \ref{def:Non-ObsTau}, $P$ necessarily makes a $\tau$ open transition and remains in the same state, ($s_p = s_{p+1}$).
+Note that, for $l\in\{1,3\}$ if $\beta_{l p j_0}=\tau$, then, because of Definition \ref{def:Non-ObsTau}, $P$ necessarily makes a $\tau$ open transition and remains in the same state, ($s_p = s_{p+1}$).
 Thus without loss of generality, we can bypass such an open transition and obtain another decomposition of the WOT without the open transition that requires ${\beta^l_{p{j_0}}}=\tau$.
-We can thus  suppose that for all $p$ and $l$ we have ${\beta^l_{p{j_0}}}\neq\tau$.
+We can thus  suppose that for all $p$ and $l$ we have ${\beta_{l p{j_0}}}\neq\tau$ or $j_0\not\in J_{1 p}$.
+To avoid a special case, we suppose that the hole $j_0$ moves during the OT $\alpha'$, i.e.
+$\beta_{2 \j_0}=\beta_{m}$ for some $m$.
+Additionally, $\beta_{m}\neq \tau$, else we would have $\alpha=\alpha'=\tau$ and the $\alpha'$ OT could be also removed from the reduction, leading to a particular and simpler case.
+
+We introduce $n_i^{i\in[0..m-1]}$, and $(n'_i)^{i\in[m+1..n]}$ the indices of the steps in 
+which the hole $j_0$ moves in the 3 sets of OTs above ($\beta_m$ is the action that matches the hole $j_0$ in the OT $\alpha'$), in other words, we have for all $i$, $\beta_{1 n_i j_0}$ a visible action, as additionally:
+\begin{equation*}
+\begin{split}
+\gamma_{j_0}&=[\beta_0..\beta_n]\\
+&=\mybigdotcup_{\substack{i=0\\j_0\in J_{1i}}}^{m_1} \vis{{\beta_{1ij_0}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{{\beta_{2j_0}}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{\substack{i=0\\j_0\in J_{3i}}}^{m_2} \vis{{\beta_{3ij_0}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\Post_{1j}}}
+\end{split}
+\end{equation*}
+
+We have, by definition of $n_i$ and $n'_i$:
+\begin{equation*}
+\begin{split}
+\forall{i\in[0..m-1]}.],&\beta_{1 n_i j_0}\subst{\bigotimes_{j=n_i-1}^{0} \Post_{1j} }=\beta_i\\ 
+&
+\beta_{2 j_0}\subst{\bigotimes_{j=m_1}^{0} \Post_{1j} }=\beta_m\\ 
+\forall{i\in[m+1..n]}.],&\beta_{3 n'_i j_0}\subst{\bigotimes_{j=n'i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\Post_{1j}}=\beta_i\\ 
+\end{split}\end{equation*}
+
+Now, we compose OTs for each of the case above (OTs of $P$)':
+\begin{enumerate}
+\item $p\in [0..m_1]$. Either there is $i$ such that $p=n_i$, and thus $\beta_i=\beta_{1 p j_0}$. In this case by Lemma~\ref{lem-Weakcompose1}, we have:
+
+Then, we have\\[-2ex]
+	\[ P[Q]_{j_0}  
+	\models
+	{\openrule
+		{
+			\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{1pj}^{j\in J_{1p}\setminus \{j_0\}}}, 
+			\Pred_{1p}\,',  \Post_{1p}\,'
+			 }
+		{\ostate{s_{1pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTWeakarrow {\tau}
+			\ostate{s_{1(p+1)j}^{\, j\in L}\uplus s_{(i+1)j}^{j\in L_Q} } }
+	}
+	\]
+with 
+\begin{mathpar}
+\Pred_{1p}\,'=\Pred_{1p}\land (\beta_{1pj_0}=\alpha_i\land \Pred_i)
+\\
+%\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
+\Post_{1p}\,'=\Post_{1p}\uplus\Post_i
+\end{mathpar}
+
+Or $j_0\not \in \dom(\beta_{1 p})$ and $Q$ does not move in the composed reduction
+\[P[Q]_{j_0} \models\openrule
+    {\set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
+         {\ostate{{(s_{1pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s_{1(p+1)i})}^{i\in L}}}
+\]
+and thus we also have a weak OT by definition:
+\[P[Q]_{j_0} \models\openrule
+    {\set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
+         {\ostate{{(s_{1pi})}^{i\in L}} \OTWeakarrow {\tau} \ostate{{(s_{1(p+1)i})}^{i\in L}}}
+\]
+\item idem for the OT $\alpha$
+\item idem for the last $]\tau$s
+\end{enumerate}
+
+What we need here is an adaptation of Lemma~\ref{lem-rel-OT-WOT} where transitions are WOTs and not OTs ... \TODO{I suggest to say that it is a trivial adaptation even if it is not}
 

### 2019-07-17 2016-Weak-FH-Bisim/WeakBisim.tex
Added TODOs for the example

--- 2019-07-15 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 \subsection{Running Example}
+\TODO{Rabea: trouver reference !!}
+\TODO{refaire les commentaires}
 To illustrate this work, we use the well-known Alternate bit protocol
@@
 
-%%\TODO{rewrite example with new OTs}
+\TODO{Eric: rewrite example with new Protocol}
 \begin{example}\emph{An open-transition.}
@@
 
-\LUDO{Je sais pas de quoi parle le prochain todo :-( l'exemple?}
-\TODO{Ceci n'est pas nouveau, n'est-ce pas, est-ce utile pour le lecteur ici ? Ou est-ce qu'on bouge tous ces ``details techniques'' dans une annexe ? Si oui, je refais avec un morceau de ABP}
-\begin{example} \emph{Using the operational rules to compute
-    open-transitions}
-  In Fig. \ref{usingrules:OT2} we show the deduction tree used to construct and prove the 
-  open transition $OT_2$ of \texttt{EnableCompL} (see example page \pageref{OT:ABP-composed}).
-  The rule uses \TrUn\ for the $\delta$ transition of $C_3$, for the $l$ transition of $C_4$, then combines the result using the $a_4$ vector of the bottom pNet node, and the $\underline{\delta(x)}$ vector of the top node.
-
-\begin{figure}[h]
-\begin{mathpar}
-  \small
-  \inferrule
-    {\inferrule
-        {0 \xrightarrow {\delta}_{C_3} 1}
-        {C_3
-          \models
-            \openrule{
-              0 \xrightarrow {\delta}_{C_3} 1,\,
-              \{\xrightarrow{\delta(x_1)}_P\},\,
-              v_1=\delta(x_1)}
-                      {\ostate{0}\OTarrow{v_1}\ostate{1}}
-        }\\
-%      \sm{fresh}v         \\
-      \inferrule%*[right={L_1}]
-        {
-%          \sm{fresh}{a_Q} \\
-          \inferrule
-              {0 \xrightarrow{l}_{C_4} 0}
-              % {\ostate{0}\xrightarrow{l}\ostate{0}}
-              {C_4
-                \models
-                \openrule{
-                      0 \xrightarrow l_{C_4} 0,\,
-                      \sm{Pred}_{C_4}}
-                      {\ostate{0}\OTarrow{l}\ostate{0}}
-              }
-        }
-        {
-          \textrm{Q>>R}\models
-              \openrule
-                  { 0 \xrightarrow {l}_{C_4} 0,\,
-                    \{\xrightarrow{acc(x_2)}_Q\},\,
-                    \ v_2=acc(x_2)
-                  }
-                  {\ostate{0}\OTarrow{v_2}\ostate{0}}
-        }   
-    }
-    {
-     \textrm{P>>(Q>>R)}
-     \models
-     \openrule
-         { 0 \xrightarrow{\delta}_{C_3} 1, \\ 0 \xrightarrow{l}_{C_4} 0,\\
-           \{\xrightarrow{\delta(x)}_P,\,\xrightarrow{acc(x)}_Q\}, \\
-            a_3=v_1 \wedge v=a_3 \wedge x_1=x_2
-           }
-         {\ostate{00} \OTarrow{v} \ostate{10}}
-      }\vspace{-4ex}
-\end{mathpar}
-  \caption{Proof of transition $OT_2$ (with interaction of processes $P$ and $Q$) for 
-  ``P>>(Q>>R)'' \TODO{Change for the new example or remove?}}
-  \label{usingrules:OT2}
-\end{figure}
-
-\end{example}
+\TODO{Add a reference to the construction (deduction tree) in the forte paper?}
+
+%% \LUDO{Je sais pas de quoi parle le prochain todo :-( l'exemple?}
+%% \TODO{Ceci n'est pas nouveau, n'est-ce pas, est-ce utile pour le lecteur ici ? Ou est-ce qu'on bouge tous ces ``details techniques'' dans une annexe ? Si oui, je refais avec un morceau de ABP}
+%% \begin{example} \emph{Using the operational rules to compute
+%%     open-transitions}
+%%   In Fig. \ref{usingrules:OT2} we show the deduction tree used to construct and prove the 
+%%   open transition $OT_2$ of \texttt{EnableCompL} (see example page \pageref{OT:ABP-composed}).
+%%   The rule uses \TrUn\ for the $\delta$ transition of $C_3$, for the $l$ transition of $C_4$, then combines the result using the $a_4$ vector of the bottom pNet node, and the $\underline{\delta(x)}$ vector of the top node.
+
+%% \begin{figure}[h]
+%% \begin{mathpar}
+%%   \small
+%%   \inferrule
+%%     {\inferrule
+%%         {0 \xrightarrow {\delta}_{C_3} 1}
+%%         {C_3
+%%           \models
+%%             \openrule{
+%%               0 \xrightarrow {\delta}_{C_3} 1,\,
+%%               \{\xrightarrow{\delta(x_1)}_P\},\,
+%%               v_1=\delta(x_1)}
+%%                       {\ostate{0}\OTarrow{v_1}\ostate{1}}
+%%         }\\
+%% %      \sm{fresh}v         \\
+%%       \inferrule%*[right={L_1}]
+%%         {
+%% %          \sm{fresh}{a_Q} \\
+%%           \inferrule
+%%               {0 \xrightarrow{l}_{C_4} 0}
+%%               % {\ostate{0}\xrightarrow{l}\ostate{0}}
+%%               {C_4
+%%                 \models
+%%                 \openrule{
+%%                       0 \xrightarrow l_{C_4} 0,\,
+%%                       \sm{Pred}_{C_4}}
+%%                       {\ostate{0}\OTarrow{l}\ostate{0}}
+%%               }
+%%         }
+%%         {
+%%           \textrm{Q>>R}\models
+%%               \openrule
+%%                   { 0 \xrightarrow {l}_{C_4} 0,\,
+%%                     \{\xrightarrow{acc(x_2)}_Q\},\,
+%%                     \ v_2=acc(x_2)
+%%                   }
+%%                   {\ostate{0}\OTarrow{v_2}\ostate{0}}
+%%         }   
+%%     }
+%%     {
+%%      \textrm{P>>(Q>>R)}
+%%      \models
+%%      \openrule
+%%          { 0 \xrightarrow{\delta}_{C_3} 1, \\ 0 \xrightarrow{l}_{C_4} 0,\\
+%%            \{\xrightarrow{\delta(x)}_P,\,\xrightarrow{acc(x)}_Q\}, \\
+%%             a_3=v_1 \wedge v=a_3 \wedge x_1=x_2
+%%            }
+%%          {\ostate{00} \OTarrow{v} \ostate{10}}
+%%       }\vspace{-4ex}
+%% \end{mathpar}
+%%   \caption{Proof of transition $OT_2$ (with interaction of processes $P$ and $Q$) for 
+%%   ``P>>(Q>>R)'' \TODO{Change for the new example or remove?}}
+%%   \label{usingrules:OT2}
+%% \end{figure}
+
+%% \end{example}
 
@@
 application of \TrDeux\ have to be fresh and all distinct. 
-This will be implemented within the open-automaton generation algorithm,
-e.g. using name generation using a global counter as a suffix.
+This is implemented within the open-automaton generation algorithm,
+using name generation using a global counter as a suffix.
 
@@
 
-\TODO{Eric: full (???) result of the tool execution on the running example}
+\TODO{Eric: full (???) result of the tool execution on the running example on the Simple Prot Spec, and maybe one example on the Impl. OTs presented in latex readable form.}
 
@@
 
-%% \TODO{ the formal view is not much interesting}
-
-%% \begin{property}[Weak open transition transitivity]
-%% Let $A$ be an open automaton, and $<J,\mathcal{S},s_0,\WT>$ a weak open automaton derived from $A$.
-%% Suppose we have the following weak open transitions in $\WT$:
-%% \[\openrule
-%%          {
-%%            \set{\gamma_1},\Pred_1,\Post_1   }
-%%          {s \OTWeakarrow {\tau} s_1}
-%% \qquad 
-%% \openrule
-%%          {
-%%            \set{\gamma_2},\Pred_2,\Post_2   }
-%%          {s_1 \OTWeakarrow {\alpha} s_2}
-%% \qquad
-%% \openrule
-%%          {
-%%            \set{\gamma_3},\Pred_3,\Post_3   }
-%%          {s_2 \OTWeakarrow {\tau} s_3}
-%% \]
-%% Then there is a weak  open transition of the following form in $\WT$:
-%% \[\openrule
-%%          {
-%%            \set{\gamma},\Pred,\Post   }
-%%          {s \OTWeakarrow {\alpha} s_3}
-%% \]
-%% Suppose additionally $\Post_3=({x_k\gets e_k})^{k\in K}$, we have the following
-%% \[
-%% \begin{array}{rcl}
-%% \gamma&=& \gamma_1\dotcup\gamma_2\dotcup\gamma_3\\
-%% \Pred&=&\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}\\
-%% \Post &=& ({x_k\gets ((e_k\subst{\Post_2})\subst{\Post_1})})^{k\in K}
-%% \end{array}\]
-%% \end{property}
+\TODO{Eric: try to draw (ATG) the weak transitino versions of the Simple Protocol, both Spec (easy) and Impl (check readability?)}
 
@@
 \subsection{Running example}
-- Detail of a $\tau^*$ sequence, \\
-- construction of the predicate\\
-- defn / elimination of the intermediate variables\\
-- construction of the weak OT.
+- If we already have shown the saturated relation, we only need to argue on bisimulation here.
+
+\TODO{Je ne pense pas que nous ayons un algo de bisim weak operationnel pour la publi, mais ca n'est pas completement impossible nonp[l;us...
+Au pire, argumenter intuitivement sur papier, en donnat les classes d'equivalence et les predicats.
+    Noter que la version de base est trop simple... Pour avoir des predicats moins triviaux, on peut ajouter un compteur qui compte le nb d'erreurs, et le transmet a la fin}
 

### 2019-07-17 2016-Weak-FH-Bisim/WeakBisim.tex
lemma 6, qques ajouts

--- 2019-07-16 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 \end{enumerate}
-By using  Lemma \ref{lem-rel-OT-WOT}, denoting $\displaystyle{J=\bigcup_{i=0}^{m_1}J_{1i}\cup J_2\cup \bigcup_{i=0}^{m_2}J_{3i}}$, we can conclude from cases 1, 2 and 3 that we have:
+By using  Lemma \ref{lem-rel-OT-WOT}, and denoting $\displaystyle{J=\bigcup_{i=0}^{m_1}J_{1i}\cup J_2\cup \bigcup_{i=0}^{m_2}J_{3i}}$, we can conclude from cases 1, 2 and 3 that we have:
 \begin{mathpar}
@@
 where:\\
-$\alpha''=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}}$
-
-We have:
+$\alpha''=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}}$\\
+On the other hand, we have:
 $\alpha=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}}\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}}}=\alpha''\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}}}$.\\
-As $\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}}}$ has no effect on variables of $P$ and thus on variables of $\alpha$, we have $\alpha=\alpha''$.
+As $\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}}}$ has no effect on variables of $P$ and thus on variables of $\alpha$, so we have $\alpha=\alpha''$.
 \\
- for all $l\in L$: 
+For all $l\in L$: 
 $s_l=s_{0l} \wedge s_{(m_1+1)l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)l}=s'_l$
@@
 ${(\gamma_j')}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}} \dotcup\\
-~~\qquad \mybigdotcup_{i=0}^{m_2}
+~~\qquad \qquad\qquad\qquad\qquad \mybigdotcup_{i=0}^{m_2}
 \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}} }\\
@@
 &\iff\bigwedge_{i=0}^{m_1}\left(\Pred'_{1p}
-		\land {\Pred''_{1p}}\land \alpha_{1p}=\beta_{1pj_0}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\right)\\
-&\qquad\land\\
-&\qquad\land\\
+		\land {\Pred''_{1p}}\land \alpha_{1p}=\beta_{1pj_0}\right)\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}} \\
+&\qquad\land\left(\Pred'_{2}
+		\land {\Pred''_{2}}\land \alpha_{2}=\beta_{2j_0}\right)\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
+&\qquad\land\bigwedge_{i=0}^{m_2} \left(\Pred'_{3p}
+		\land {\Pred''_{3p}}\land \alpha_{3p}=\beta_{3pj_0}\right) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
 &\iff\bigwedge_{i=0}^{m_1}\left((\Pred'_{1p}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}})
-		\land ({\Pred''_{1p}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post''_{1j}})\land (\alpha_{1p}=\beta_{1pj_0}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}})\right)\\
-&\qquad\land\\
-&\qquad\land\\
+		\land ({\Pred''_{1p}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post''_{1j}})\land (\alpha_{1p}=\beta_{1pj_0})\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\right) \\
+&\qquad\land \left(\Pred'_{2}\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}
+		\land {\Pred''_{2}} \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \land (\alpha_{2}=\beta_{2j_0})\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \right) \\
+&\qquad\land\bigwedge_{i=0}^{m_2} \left(\Pred'_{3p} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} 
+		\land {\Pred''_{3p}} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \right ) \\
+		 & \qquad \land (\alpha_{3p}=\beta_{3pj_0}) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}  \\
 &\iff \Pred'\land\bigwedge_{k=0}^n\Pred_k\bigotimes_{j=k-1}^{0}\!\!\Post_{j}\land\Pred_\beta
@@
 }
-Which is exactly what is needed.
-
-Finally we have
+which is exactly what is needed.\\
+Finally we have:
 \[\Post=\Post\,' \uplus \bigotimes_{p=n}^0
@@
 \Post&=\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}\\
-&=\bigotimes_{j=m_2}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}\\
-&\qquad \uplus \bigotimes_{j=m_2}^{0}\!\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}\\
+&=\bigotimes_{j=m_2}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j} \uplus \bigotimes_{j=m_2}^{0}\!\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}\\
 &=\Post' \uplus \bigotimes_{j=n'_{n+1}-1}^{0}\!\!\Post''_{j}

### 2019-07-17 2016-Weak-FH-Bisim/WeakBisim.tex
new todo

--- 2019-07-17 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 \subsection{Running Example}
-\TODO{Rabea: trouver reference !!}
-\TODO{refaire les commentaires}
 To illustrate this work, we use the well-known Alternate bit protocol
@@
 
-\TODO{Eric: rewrite example with new Protocol}
+%%\TODO{rewrite example with new OTs}
 \begin{example}\emph{An open-transition.}
@@
 
-\TODO{Add a reference to the construction (deduction tree) in the forte paper?}
-
-%% \LUDO{Je sais pas de quoi parle le prochain todo :-( l'exemple?}
-%% \TODO{Ceci n'est pas nouveau, n'est-ce pas, est-ce utile pour le lecteur ici ? Ou est-ce qu'on bouge tous ces ``details techniques'' dans une annexe ? Si oui, je refais avec un morceau de ABP}
-%% \begin{example} \emph{Using the operational rules to compute
-%%     open-transitions}
-%%   In Fig. \ref{usingrules:OT2} we show the deduction tree used to construct and prove the 
-%%   open transition $OT_2$ of \texttt{EnableCompL} (see example page \pageref{OT:ABP-composed}).
-%%   The rule uses \TrUn\ for the $\delta$ transition of $C_3$, for the $l$ transition of $C_4$, then combines the result using the $a_4$ vector of the bottom pNet node, and the $\underline{\delta(x)}$ vector of the top node.
-
-%% \begin{figure}[h]
-%% \begin{mathpar}
-%%   \small
-%%   \inferrule
-%%     {\inferrule
-%%         {0 \xrightarrow {\delta}_{C_3} 1}
-%%         {C_3
-%%           \models
-%%             \openrule{
-%%               0 \xrightarrow {\delta}_{C_3} 1,\,
-%%               \{\xrightarrow{\delta(x_1)}_P\},\,
-%%               v_1=\delta(x_1)}
-%%                       {\ostate{0}\OTarrow{v_1}\ostate{1}}
-%%         }\\
-%% %      \sm{fresh}v         \\
-%%       \inferrule%*[right={L_1}]
-%%         {
-%% %          \sm{fresh}{a_Q} \\
-%%           \inferrule
-%%               {0 \xrightarrow{l}_{C_4} 0}
-%%               % {\ostate{0}\xrightarrow{l}\ostate{0}}
-%%               {C_4
-%%                 \models
-%%                 \openrule{
-%%                       0 \xrightarrow l_{C_4} 0,\,
-%%                       \sm{Pred}_{C_4}}
-%%                       {\ostate{0}\OTarrow{l}\ostate{0}}
-%%               }
-%%         }
-%%         {
-%%           \textrm{Q>>R}\models
-%%               \openrule
-%%                   { 0 \xrightarrow {l}_{C_4} 0,\,
-%%                     \{\xrightarrow{acc(x_2)}_Q\},\,
-%%                     \ v_2=acc(x_2)
-%%                   }
-%%                   {\ostate{0}\OTarrow{v_2}\ostate{0}}
-%%         }   
-%%     }
-%%     {
-%%      \textrm{P>>(Q>>R)}
-%%      \models
-%%      \openrule
-%%          { 0 \xrightarrow{\delta}_{C_3} 1, \\ 0 \xrightarrow{l}_{C_4} 0,\\
-%%            \{\xrightarrow{\delta(x)}_P,\,\xrightarrow{acc(x)}_Q\}, \\
-%%             a_3=v_1 \wedge v=a_3 \wedge x_1=x_2
-%%            }
-%%          {\ostate{00} \OTarrow{v} \ostate{10}}
-%%       }\vspace{-4ex}
-%% \end{mathpar}
-%%   \caption{Proof of transition $OT_2$ (with interaction of processes $P$ and $Q$) for 
-%%   ``P>>(Q>>R)'' \TODO{Change for the new example or remove?}}
-%%   \label{usingrules:OT2}
-%% \end{figure}
-
-%% \end{example}
+\LUDO{Je sais pas de quoi parle le prochain todo :-( l'exemple?}
+\TODO{Ceci n'est pas nouveau, n'est-ce pas, est-ce utile pour le lecteur ici ? Ou est-ce qu'on bouge tous ces ``details techniques'' dans une annexe ? Si oui, je refais avec un morceau de ABP}
+\begin{example} \emph{Using the operational rules to compute
+    open-transitions}
+  In Fig. \ref{usingrules:OT2} we show the deduction tree used to construct and prove the 
+  open transition $OT_2$ of \texttt{EnableCompL} (see example page \pageref{OT:ABP-composed}).
+  The rule uses \TrUn\ for the $\delta$ transition of $C_3$, for the $l$ transition of $C_4$, then combines the result using the $a_4$ vector of the bottom pNet node, and the $\underline{\delta(x)}$ vector of the top node.
+
+\begin{figure}[h]
+\begin{mathpar}
+  \small
+  \inferrule
+    {\inferrule
+        {0 \xrightarrow {\delta}_{C_3} 1}
+        {C_3
+          \models
+            \openrule{
+              0 \xrightarrow {\delta}_{C_3} 1,\,
+              \{\xrightarrow{\delta(x_1)}_P\},\,
+              v_1=\delta(x_1)}
+                      {\ostate{0}\OTarrow{v_1}\ostate{1}}
+        }\\
+%      \sm{fresh}v         \\
+      \inferrule%*[right={L_1}]
+        {
+%          \sm{fresh}{a_Q} \\
+          \inferrule
+              {0 \xrightarrow{l}_{C_4} 0}
+              % {\ostate{0}\xrightarrow{l}\ostate{0}}
+              {C_4
+                \models
+                \openrule{
+                      0 \xrightarrow l_{C_4} 0,\,
+                      \sm{Pred}_{C_4}}
+                      {\ostate{0}\OTarrow{l}\ostate{0}}
+              }
+        }
+        {
+          \textrm{Q>>R}\models
+              \openrule
+                  { 0 \xrightarrow {l}_{C_4} 0,\,
+                    \{\xrightarrow{acc(x_2)}_Q\},\,
+                    \ v_2=acc(x_2)
+                  }
+                  {\ostate{0}\OTarrow{v_2}\ostate{0}}
+        }   
+    }
+    {
+     \textrm{P>>(Q>>R)}
+     \models
+     \openrule
+         { 0 \xrightarrow{\delta}_{C_3} 1, \\ 0 \xrightarrow{l}_{C_4} 0,\\
+           \{\xrightarrow{\delta(x)}_P,\,\xrightarrow{acc(x)}_Q\}, \\
+            a_3=v_1 \wedge v=a_3 \wedge x_1=x_2
+           }
+         {\ostate{00} \OTarrow{v} \ostate{10}}
+      }\vspace{-4ex}
+\end{mathpar}
+  \caption{Proof of transition $OT_2$ (with interaction of processes $P$ and $Q$) for 
+  ``P>>(Q>>R)'' \TODO{Change for the new example or remove?}}
+  \label{usingrules:OT2}
+\end{figure}
+
+\end{example}
 
@@
 application of \TrDeux\ have to be fresh and all distinct. 
-This is implemented within the open-automaton generation algorithm,
-using name generation using a global counter as a suffix.
+This will be implemented within the open-automaton generation algorithm,
+e.g. using name generation using a global counter as a suffix.
 
@@
 
-\TODO{Eric: full (???) result of the tool execution on the running example on the Simple Prot Spec, and maybe one example on the Impl. OTs presented in latex readable form.}
+\TODO{Eric: full (???) result of the tool execution on the running example}
 
@@
 
-\TODO{Eric: try to draw (ATG) the weak transitino versions of the Simple Protocol, both Spec (easy) and Impl (check readability?)}
+%% \TODO{ the formal view is not much interesting}
+
+%% \begin{property}[Weak open transition transitivity]
+%% Let $A$ be an open automaton, and $<J,\mathcal{S},s_0,\WT>$ a weak open automaton derived from $A$.
+%% Suppose we have the following weak open transitions in $\WT$:
+%% \[\openrule
+%%          {
+%%            \set{\gamma_1},\Pred_1,\Post_1   }
+%%          {s \OTWeakarrow {\tau} s_1}
+%% \qquad 
+%% \openrule
+%%          {
+%%            \set{\gamma_2},\Pred_2,\Post_2   }
+%%          {s_1 \OTWeakarrow {\alpha} s_2}
+%% \qquad
+%% \openrule
+%%          {
+%%            \set{\gamma_3},\Pred_3,\Post_3   }
+%%          {s_2 \OTWeakarrow {\tau} s_3}
+%% \]
+%% Then there is a weak  open transition of the following form in $\WT$:
+%% \[\openrule
+%%          {
+%%            \set{\gamma},\Pred,\Post   }
+%%          {s \OTWeakarrow {\alpha} s_3}
+%% \]
+%% Suppose additionally $\Post_3=({x_k\gets e_k})^{k\in K}$, we have the following
+%% \[
+%% \begin{array}{rcl}
+%% \gamma&=& \gamma_1\dotcup\gamma_2\dotcup\gamma_3\\
+%% \Pred&=&\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}\\
+%% \Post &=& ({x_k\gets ((e_k\subst{\Post_2})\subst{\Post_1})})^{k\in K}
+%% \end{array}\]
+%% \end{property}
 
@@
 \subsection{Running example}
-- If we already have shown the saturated relation, we only need to argue on bisimulation here.
-
-\TODO{Je ne pense pas que nous ayons un algo de bisim weak operationnel pour la publi, mais ca n'est pas completement impossible nonp[l;us...
-Au pire, argumenter intuitivement sur papier, en donnat les classes d'equivalence et les predicats.
-    Noter que la version de base est trop simple... Pour avoir des predicats moins triviaux, on peut ajouter un compteur qui compte le nb d'erreurs, et le transmet a la fin}
+- Detail of a $\tau^*$ sequence, \\
+- construction of the predicate\\
+- defn / elimination of the intermediate variables\\
+- construction of the weak OT.
 
@@
 
+\TODO{I think the rest is useless (old proof sketch)}
+
 Moreover, we have for all $t\in[0..n]$:

### 2019-07-17 2016-Weak-FH-Bisim/WeakBisim.tex
Skype meeting

--- 2019-07-17 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 \text{and\qquad }
- \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigotimes_{i=p-1}^{0}\Post_i)} \\
+ \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigotimes_{i=p-1}^{0}\Post_i} \\
  \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\
 {\hspace{-3ex}}\text{and~~} \Pred \iff \Pred\,'
-		\land \!\!\bigwedge_{p=0}^n((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} )
+		\land \!\!\bigwedge_{p=0}^n(\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i} = \beta_p\land \Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i} )
 \\
@@
 
-Also note that for all $k\in[0..n-1]$, $v_{kl}'=v_{(k+1)l}$, and $v_{0l}=s_{0l}=s_l$ and $v'_{nl}=v_{(n_1+n_2+3) l}=u_{n_2 l} = s'_l$.
+Note that for all $k\in[0..n-1]$, $v_{kl}'=v_{(k+1)l}$, and $v_{0l}=s_{0l}=s_l$ and $v'_{nl}=v_{(n_1+n_2+3) l}=u_{(n_2+1) l} = s'_l$.
+
+By definition of $\Post_k$, we have $\displaystyle{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j} = \bigotimes_{j=k-1}^{0}\!\!\Post_{j}}$
 
@@
 %might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.\\
-Note that \[\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{j}}} =
+Consequently \[\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{j}}} =
 \alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post''_{j}\otimes\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j}}} = \alpha_k'\displaystyle{\subst{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j}}} =
@@
 
-And thus, because $\beta_{pj}^{j\in J\cap \Holes(Q)}$ are equal to  $(\beta'_{1pj})^{j\in J\cap \Holes(Q)}$, $(\beta'_{2j})^{j\in J\cap \Holes(Q)}$, and $(\beta')_{3pj}^{j\in J\cap \Holes(Q)}$ (re-indexed), and additionally $(\beta')_{1pj}^{j\in J\cap \Holes(Q)}$, $(\beta')_{2j}^{j\in J\cap \Holes(Q)}$, and $(\beta')_{3pj}^{j\in J\cap \Holes(Q)}$ are identical to the holes labels $\beta_{1kj}^{j\in J\cap \Holes(Q)}$, $\beta_{2j}^{j\in J\cap \Holes(Q)}$, and $\beta_{3kj}^{j\in J\cap \Holes(Q)}$ when $Q$ moves\footnote{more precisely, when $Q$ moves either $\beta_{1kj}^{j\in J\cap \Holes(Q)}$ is not empty  and thus $(\beta')_{1pj}^{j\in J\cap \Holes(Q)}=\beta_{1kj}^{j\in J\cap \Holes(Q)}$, or both are empty if the holes perform no action}.
+And thus, because $\beta_{pj}^{j\in J\cap \Holes(Q)}$ are equal to the concatenation of  $(\beta'_{1pj})^{j\in J\cap \Holes(Q)}$, $(\beta'_{2j})^{j\in J\cap \Holes(Q)}$, and $(\beta_{3pj}')^{j\in J\cap \Holes(Q)}$ (re-indexed because we skipped some transitions), and additionally $(\beta_{1pj}')^{j\in J\cap \Holes(Q)}$, $(\beta_{2j}')^{j\in J\cap \Holes(Q)}$, and $(\beta_{3pj}')^{j\in J\cap \Holes(Q)}$ are identical to the hole labels $\beta_{1kj}^{j\in J\cap \Holes(Q)}$, $\beta_{2j}^{j\in J\cap \Holes(Q)}$, and $\beta_{3kj}^{j\in J\cap \Holes(Q)}$ (re-indexed) when $Q$ moves\footnote{more precisely, when $Q$ moves either $\beta_{1kj}^{j\in J\cap \Holes(Q)}$ is not empty  and thus $(\beta_{1pj}')^{j\in J\cap \Holes(Q)}=\beta_{1kj}^{j\in J\cap \Holes(Q)}$, or both are empty if the holes of $Q$ perform no action}.
 We can assert a similar equality on postconditions, i.e.
@@
 \begin{split}
-\gamma_j^{j\in J\cap \Holes(Q)}&=\mybigdotcup_{i=0}^{m_1} \vis{\set{(\beta')_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!
+\gamma_j^{j\in J\cap \Holes(Q)}&=\mybigdotcup_{i=0}^{m_1} \vis{\set{(\beta_{1i}')}\subst{\bigotimes_{j=i-1}^{0}\!\!
 \Post''_{1j}}}\dotcup  \vis{\set{\beta'_2}\subst{\bigotimes_{j=m_1}^{0}\Post''_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}} }\\
-&=\mybigdotcup_{k=0}^n \left( \mybigdotcup_{i=n'_k}^{n'_{k+1}-1}\beta_{ij}^{j\in J\cap \Holes(Q)}\subst{\bigotimes_{j=i-1}^{n'_k}\!\!\Post''_{j}\bigotimes_{j=n'_k-1}^{0}\!\!\Post''_{j}}\right)\\
+&=\mybigdotcup_{k=0}^n \left( \mybigdotcup_{i=n'_k}^{n'_{k+1}-1}\vis{\beta_{ij}^{j\in J\cap \Holes(Q)}\subst{\bigotimes_{j=i-1}^{n'_k}\!\!\Post''_{j}\bigotimes_{j=n'_k-1}^{0}\!\!\Post''_{j}}}\right)\\
 &=\mybigdotcup_{k=0}^n \left( \gamma_{kj}^{j\in J\cap \Holes(Q)}\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{k}}\right)
@@
 		\land {\Pred''_{2}} \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \land (\alpha_{2}=\beta_{2j_0})\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \right) \\
-&\qquad\land\bigwedge_{i=0}^{m_2} \left(\Pred'_{3p} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} 
-		\land {\Pred''_{3p}} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \right ) \\
-		 & \qquad \land (\alpha_{3p}=\beta_{3pj_0}) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}  \\
+&\qquad\land\bigwedge_{i=0}^{m_2} \Bigg(\Pred'_{3p} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} 
+		\land {\Pred''_{3p}} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}  \\
+		 & \qquad \land (\alpha_{3p}=\beta_{3pj_0}) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\Bigg)  \\
 &\iff \Pred'\land\bigwedge_{k=0}^n\Pred_k\bigotimes_{j=k-1}^{0}\!\!\Post_{j}\land\Pred_\beta
@@
 \\
-\Pred_Q=\bigwedge_{h=0}^{k}\!\big(\Pred_{1h}\bigotimes_{j=h-1}^{0}\subst{\Post_j^1}\big)\land \Pred_2\bigotimes_{h=k}^{0}\subst{\Post_{1h}}\land\\~\qquad\qquad \bigwedge_{h=0}^{k'}\!\Pred_{3h}\big(\bigotimes_{j=h-1}^{0}\subst{\Post_{3j}}\subst{\Post_2}  \bigotimes_{h=k}^{0}\subst{\Post_{1h}}\big)
+\Pred_Q=\bigwedge_{h=0}^{k}\!\big(\Pred_{1h}\subst{\bigotimes_{j=h-1}^{0}\Post_j^1}\big)\land \Pred_2\subst{\bigotimes_{h=k}^{0}\Post_{1h}}\land\\~\qquad\qquad \bigwedge_{h=0}^{k'}\!\Pred_{3h}\subst{\bigotimes_{j=h-1}^{0}{\Post_{3j}}\otimes{\Post_2}  \otimes\bigotimes_{h=k}^{0}\Post_{1h}}
 \\
-\Post_Q=\bigotimes_{h=k'}^{0}\Post_{3h}\subst{\Post_2}\bigotimes_{j=k}^{0}\subst{\Post_{1j}}
+\Post_Q=\bigotimes_{h=k'}^{0}\Post_{3h}\otimes\Post_2\otimes\bigotimes_{j=k}^{0}\Post_{1j}
 $
@@
 \Pred_c&=\Pred_Q\land\Pred\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land
-(\alpha'_Q=\beta_{j_0})subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\\
+(\alpha'_Q=\beta_{j_0})\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\\
 &=\Pred_Q\land\Pred\land \alpha_Q=\beta_{j_0}
@@
 \item idem for the OT $\alpha$
-\item idem for the last $]\tau$s
+\item idem for the last $\tau$s
 \end{enumerate}
@@
 What we need here is an adaptation of Lemma~\ref{lem-rel-OT-WOT} where transitions are WOTs and not OTs ... \TODO{I suggest to say that it is a trivial adaptation even if it is not}
+
+\TODO{I think the rest is useless (old proof sketch)}
 

### 2019-07-17 2016-Weak-FH-Bisim/WeakBisim.tex
nouveau dessins page 9

--- 2019-07-17 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 \begin{figure}[t]
-  \centerline{
-   \includegraphics[width=8cm]{XFIG/SimpleProt-Schema}
-   }
-   \caption{Schema of the Simple Protocol Example}  \label{SimpleProt:Schema}
+   \includegraphics[width=5.5cm]{XFIG/SimpleProt-Schema}
+   \includegraphics[width=6.5cm]{XFIG/SimpleProt-Spec}
+   \caption{Specification pNet Schema and Specification}
+   \label{SimpleProt:Spec}
+
 \end{figure}
@@
 \begin{figure}[t]
-%\begin{minipage}{\linewidth}
-
- %%  \includegraphics[width=7cm]{XFIG/Transport}
- %%  \hspace{0.5cm}
- %% \includegraphics[width=4.5cm]{XFIG/TransportSpec}
- %%  \caption{\TODO{Replace by various versions of the media} }  \label{schema:ABP-pnets}
-
-  %% \centerline{
-  %%  \includegraphics[width=3.5cm]{XFIG/PerfectMedium}
-  %%  \hspace{0.5cm}
-  %%  \includegraphics[width=4cm]{XFIG/FaultyMedium}
-  %%  }
-  %%  \caption{Perfect and faulty (loosing and duplicating) media}  \label{schema:ABP-media}
-
-  %\end{minipage}
-%  \vspace{1cm}
-%\begin{minipage}{6cm}
-  \centerline{\includegraphics[width=11cm]{XFIG/SimpleProt-pNet}}
-  \caption{Composed pNet with the Simple Protocol}  \label{schema:SimpleProt-composed}
-%\end{minipage}
-
+  \centerline{\includegraphics[width=12cm]{XFIG/SimpleProt-pNet}}
+  \caption{Composed pNet with the Simple Protocol Implementation}  \label{SimpleProt:Impl}
 \end{figure}
@@
 \end{enumerate}
-By using  Lemma \ref{lem-rel-OT-WOT}, and denoting $\displaystyle{J=\bigcup_{i=0}^{m_1}J_{1i}\cup J_2\cup \bigcup_{i=0}^{m_2}J_{3i}}$, we can conclude from cases 1, 2 and 3 that we have:
+By using  Lemma \ref{lem-rel-OT-WOT}, denoting $\displaystyle{J=\bigcup_{i=0}^{m_1}J_{1i}\cup J_2\cup \bigcup_{i=0}^{m_2}J_{3i}}$, we can conclude from cases 1, 2 and 3 that we have:
 \begin{mathpar}
@@
 where:\\
-$\alpha''=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}}$\\
-On the other hand, we have:
+$\alpha''=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}}$
+
+We have:
 $\alpha=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}}\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}}}=\alpha''\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}}}$.\\
-As $\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}}}$ has no effect on variables of $P$ and thus on variables of $\alpha$, so we have $\alpha=\alpha''$.
+As $\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}}}$ has no effect on variables of $P$ and thus on variables of $\alpha$, we have $\alpha=\alpha''$.
 \\
-For all $l\in L$: 
+ for all $l\in L$: 
 $s_l=s_{0l} \wedge s_{(m_1+1)l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)l}=s'_l$
@@
 ${(\gamma_j')}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}} \dotcup\\
-~~\qquad \qquad\qquad\qquad\qquad \mybigdotcup_{i=0}^{m_2}
+~~\qquad \mybigdotcup_{i=0}^{m_2}
 \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}} }\\
@@
 &\iff\bigwedge_{i=0}^{m_1}\left(\Pred'_{1p}
-		\land {\Pred''_{1p}}\land \alpha_{1p}=\beta_{1pj_0}\right)\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}} \\
-&\qquad\land\left(\Pred'_{2}
-		\land {\Pred''_{2}}\land \alpha_{2}=\beta_{2j_0}\right)\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
-&\qquad\land\bigwedge_{i=0}^{m_2} \left(\Pred'_{3p}
-		\land {\Pred''_{3p}}\land \alpha_{3p}=\beta_{3pj_0}\right) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
+		\land {\Pred''_{1p}}\land \alpha_{1p}=\beta_{1pj_0}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\right)\\
+&\qquad\land\\
+&\qquad\land\\
 &\iff\bigwedge_{i=0}^{m_1}\left((\Pred'_{1p}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}})
-		\land ({\Pred''_{1p}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post''_{1j}})\land (\alpha_{1p}=\beta_{1pj_0})\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\right) \\
-&\qquad\land \left(\Pred'_{2}\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}
-		\land {\Pred''_{2}} \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \land (\alpha_{2}=\beta_{2j_0})\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \right) \\
-&\qquad\land\bigwedge_{i=0}^{m_2} \left(\Pred'_{3p} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} 
-		\land {\Pred''_{3p}} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \right ) \\
-		 & \qquad \land (\alpha_{3p}=\beta_{3pj_0}) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}  \\
+		\land ({\Pred''_{1p}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post''_{1j}})\land (\alpha_{1p}=\beta_{1pj_0}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}})\right)\\
+&\qquad\land\\
+&\qquad\land\\
 &\iff \Pred'\land\bigwedge_{k=0}^n\Pred_k\bigotimes_{j=k-1}^{0}\!\!\Post_{j}\land\Pred_\beta
@@
 }
-which is exactly what is needed.\\
-Finally we have:
+Which is exactly what is needed.
+
+Finally we have
 \[\Post=\Post\,' \uplus \bigotimes_{p=n}^0
@@
 \Post&=\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}\\
-&=\bigotimes_{j=m_2}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j} \uplus \bigotimes_{j=m_2}^{0}\!\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}\\
+&=\bigotimes_{j=m_2}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}\\
+&\qquad \uplus \bigotimes_{j=m_2}^{0}\!\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}\\
 &=\Post' \uplus \bigotimes_{j=n'_{n+1}-1}^{0}\!\!\Post''_{j}

### 2019-07-17 2016-Weak-FH-Bisim/WeakBisim.tex
petites corrections+figure

--- 2019-07-17 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
-\item Finally, for the open transition $\symb{OT}$ in the form ($\set{\beta_{2}}=\beta_{2j}^{j\in J_2}$): $P[Q]_{j_0}	\models \openrule
+\item Finally, for the open transition in the form ($\set{\beta_{2}}=\beta_{2j}^{j\in J_2}$): $P[Q]_{j_0}	\models \openrule
          {
@@
 By considering $\tau$  actions we split the sequence of actions into $n+1$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.
-We can decompose each of the $n+1$ subsequences; for $k\in [0..n]$ the position of the $k^{\text{th}}$ visible action is  $n_k$, for $k\in [1..n]$,  $n'_k$ is any index between $n_{k-1}$ and $n_k$, additionally $n'_0=0$ and $n'_{n+1}=n_1+n_2+3$.
+We can decompose each of the $n+1$ subsequences;
+
+\includegraphics[width=6cm]{XFIG/proof-explain}
+
+for $k\in [0..n]$ the position of the $k^{\text{th}}$ visible action is  $n_k$, for $k\in [1..n]$,  $n'_k$ is any index between $n_{k-1}$ and $n_k$, additionally $n'_0=0$ and $n'_{n+1}=n_1+n_2+3$.
 We obtain $n+1$ subsequences  made of the following OTs, for all $k\in [0..n]$ :\\
@@
 $\displaystyle{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=\displaystyle{\mybigdotcup_{i=n'_{k}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k}}\!\!\!\Post''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post''_{l}}}} \dotcup\\
-~~\qquad \mybigdotcup_{i=n_k+1}^{n'_{k+1}-1}
+~~\qquad \qquad\qquad\mybigdotcup_{i=n_k+1}^{n'_{k+1}-1}
 \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}} \subst{\bigotimes_{l=i-1}^{n_k\!+\!1}\!\Post''_{l}\shortotimes\Post''_{n_k}\shortotimes\!\!\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post''_{l}} }\\
@@
 
-Note that for all $k\in[0..n-1]$, $v_{kl}'=v_{(k+1)l}$, and $v_{0l}=s_{0l}=s_l$ and $v'_{nl}=v_{(n_1+n_2+3) l}=u_{(n_2+1) l} = s'_l$.
-
-By definition of $\Post_k$, we have $\displaystyle{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j} = \bigotimes_{j=k-1}^{0}\!\!\Post_{j}}$
-
+Note that for all $k\in[0..n-1]$, $v_{kl}'=v_{(k+1)l}$,  $v_{0l}=s_{0l}=s_l$, and $v'_{nl}=v_{(n_1+n_2+3) l}=u_{(n_2+1) l} = s'_l$.
+
+By definition of $\Post_k$, we have $\displaystyle{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j} = \bigotimes_{j=k-1}^{0}\!\!\Post_{j}}$.
 %In this case, the number of weak open transitions
 %might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.\\
-Consequently \[\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{j}}} =
+Consequently,  we have:
+\[\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{j}}} =
 \alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post''_{j}\otimes\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j}}} = \alpha_k'\displaystyle{\subst{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j}}} =
@@
 \bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
-&\iff\bigwedge_{i=0}^{m_1}\left(\Pred'_{1p}
-		\land {\Pred''_{1p}}\land \alpha_{1p}=\beta_{1pj_0}\right)\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}} \\
+&\iff\bigwedge_{i=0}^{m_1}\left(\Pred'_{1i}
+		\land {\Pred''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}\right)\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}} \\
 &\qquad\land\left(\Pred'_{2}
 		\land {\Pred''_{2}}\land \alpha_{2}=\beta_{2j_0}\right)\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
-&\qquad\land\bigwedge_{i=0}^{m_2} \left(\Pred'_{3p}
-		\land {\Pred''_{3p}}\land \alpha_{3p}=\beta_{3pj_0}\right) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
-&\iff\bigwedge_{i=0}^{m_1}\left((\Pred'_{1p}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}})
-		\land ({\Pred''_{1p}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post''_{1j}})\land (\alpha_{1p}=\beta_{1pj_0})\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\right) \\
+&\qquad\land\bigwedge_{i=0}^{m_2} \left(\Pred'_{3i}
+		\land {\Pred''_{3i}}\land \alpha_{3i}=\beta_{3ij_0}\right) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
+&\iff\bigwedge_{i=0}^{m_1}\left((\Pred'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}})
+		\land ({\Pred''_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post''_{1j}})\land (\alpha_{1i}=\beta_{1ij_0})\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\right) \\
 &\qquad\land \left(\Pred'_{2}\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}
 		\land {\Pred''_{2}} \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \land (\alpha_{2}=\beta_{2j_0})\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \right) \\
-&\qquad\land\bigwedge_{i=0}^{m_2} \Bigg(\Pred'_{3p} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} 
-		\land {\Pred''_{3p}} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}  \\
-		 & \qquad \land (\alpha_{3p}=\beta_{3pj_0}) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\Bigg)  \\
-&\iff \Pred'\land\bigwedge_{k=0}^n\Pred_k\bigotimes_{j=k-1}^{0}\!\!\Post_{j}\land\Pred_\beta
-\\&\iff \Pred'\land\bigwedge_{k=0}^n\Pred_k\bigotimes_{j=k-1}^{0}\!\!\Post_{j}\land
-(\gamma_{j_0}=[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n]])
+&\qquad\land\bigwedge_{i=0}^{m_2} \Bigg(\Pred'_{3i} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} 
+		\land {\Pred''_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}  \\
+		 & \qquad \land (\alpha_{3i}=\beta_{3ij_0}) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\Bigg)  \\
+&\iff \Pred'\land\bigwedge_{k=0}^n\Pred_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}\land\Pred_\beta
+\\&\iff \Pred'\land\bigwedge_{k=0}^n\Pred_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}\land
+(\gamma_{j_0}=[\alpha'_{i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{j}}|i\in[0..n]])
 \end{split}\end{equation*}

### 2019-07-19 2016-Weak-FH-Bisim/WeakBisim.tex
qques corrections

@@
 \\
-		\text{and~\qquad}  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) 
+		\text{such that~\qquad}  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) 
+\text{, }
+ \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigotimes_{i=p-1}^{0}\Post_i}, \\
+{~\hspace{2cm}}\Pred \iff \Pred\,'
+		\land \!\!\bigwedge_{p=0}^n(\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i} = \beta_p\land \Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i} ),
 \\
-\text{and\qquad }
- \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigotimes_{i=p-1}^{0}\Post_i} \\
- \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\
-{\hspace{-3ex}}\text{and~~} \Pred \iff \Pred\,'
-		\land \!\!\bigwedge_{p=0}^n(\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i} = \beta_p\land \Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i} )
-\\
-\text{and~}
-\Post=\Post\,' \uplus \bigotimes_{p=n}^0
-		\Post_p  
+{~\hspace{2cm}}\Post=\Post\,' \uplus \bigotimes_{p=n}^0
+		\Post_p,   \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\
 		\end{mathpar} 
@@
 }
-\[\forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i \text{see above}\]
-
-\[ \Pred = \Pred\,'
-		\land \!\!\bigwedge_{p=0}^n((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} )\]
+$\forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i$ (see above)\\
+$\Pred = \displaystyle{\Pred\,'
+		\land \!\!\bigwedge_{p=0}^n((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} )}$
 
@@
 which is exactly what is needed.\\
-Finally we have:
-\[\Post=\Post\,' \uplus \bigotimes_{p=n}^0
-		\Post_p  \]
+Finally we have:\\
+$\Post=\displaystyle{\Post\,' \uplus \bigotimes_{p=n}^0
+		\Post_p}$\\
 Because
@@
 		\ostate{(s_i')^{\, i\in L}}}
-}\\
-\text{~~and~~}
+}
+\quad\text{~~and~~}\quad
 Q\models{\openrule
@@
 %\qquad
-\Pred\,'=\Pred\land (\beta_{j_0}=\alpha_Q\land \Pred_Q)
-\\
+\Pred\,'=\Pred\land (\beta_{j_0}=\alpha_Q\land \Pred_Q) \quad\text{~~and~~}\quad
 %\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
@@
 By  Lemma \ref{lem-rel-OT-WOT} we can decompose the WOT of $Q$ into  a series of $k+1$ and $k'+1$ tau open transitions and an observable open transition:
-
-\[\forall h\!\in\![0..k].Q\models\openrule
+\begin{mathpar}
+\forall h\!\in\![0..k].Q\models\openrule
     {\set{\beta_{1h}},\Pred_{1h},\Post_{1h}   }
-         {\ostate{{(s_{1h})}} \OTarrow {\tau} \ostate{{(s_{1(h+1)})}}}
-\]
-
-\[Q\models{\openrule
+         {\ostate{{(s_{1h})}} \OTarrow {\tau} \ostate{{(s_{1(h+1)})}}}, \quad
+Q\models{\openrule
 	{
@@
 		\ostate{s_{21}}}
-}
-\]
-
-\[
+}, \\ \quad\text{~~and~~}\quad 
 \forall h \in [0..k'].Q\models\openrule
@@
            \set{\beta_{3h}},\Pred_{3h}, \Post_{3h}}
-         { \ostate{(s_{3h})} \OTarrow {\tau} \ostate{(s_{3(h+1)})}} \]
-
-such that 
+         { \ostate{(s_{3h})} \OTarrow {\tau} \ostate{(s_{3(h+1)})}}
+\end{mathpar}
+such that\\ 
 $\alpha_Q=\alpha'_Q\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$\\
 $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\
-
 $\displaystyle{\set{\gamma}=\mybigdotcup_{h=0}^{k} \vis{\set{\beta_{1h}}} \dotcup  \vis{\set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}}}}
@@
 
-By Lemma \ref{lem-rel-OT-WOT} from cases $(1)$, $(2)$ and $(3)$ we obtain: 
+Using Lemma \ref{lem-rel-OT-WOT}, from cases $(1)$, $(2)$ and $(3)$ we get: 
 \[P[Q]_{j_0}\!\models		
@@
 	\ostate{{{s'}^{i\in L}_{i}\uplus s_{3(k'+1)}}}}\] 
-where
-\[\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}} \]
-and $\alpha=\alpha'$  because $\Post_{1j}$ acts on variables of $Q$ and $\alpha$ contains only variables of $P$
-
-\[\set{\gamma'}=\mybigdotcup_{h=0}^k\vis{\set{\beta_{1h}}} \dotcup \vis{{\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'}\vis{\set{\beta_{3h}}}=\set{\gamma}\uplus\vis{\beta_j^{j\in J\setminus \{j_0\}}}\]
-\[
-\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_i{1i}}\land
+where\\
+$\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$
+and $\alpha=\alpha'$  because $\Post_{1j}$ acts on variables of $Q$ and $\alpha$ contains only variables of $P$.\\
+
+$\set{\gamma'}=\mybigdotcup_{h=0}^k\vis{\set{\beta_{1h}}} \dotcup \vis{{\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'}\vis{\set{\beta_{3h}}}=\set{\gamma}\uplus\vis{\beta_j^{j\in J\setminus \{j_0\}}}$\\
+$\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_i{1i}}\land
 \left(Pred\land\Pred_2\land \alpha'_Q=\beta_{j_0 }\right)\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land\\\displaystyle
@@
 \end{array}
-\]
-
-\[\Post_c=(\bigotimes_{i=k'}^{0}{\Post_{3i}})\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}
-\]
+$\\
+$\Post_c=\displaystyle{(\bigotimes_{i=k'}^{0}{\Post_{3i}})\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}$
+
 Note that we have $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\

### 2019-07-19 2016-Weak-FH-Bisim/WeakBisim.tex
qques corrections
lemma 8 again

--- 2019-07-17 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
-\item Finally, for the open transition in the form ($\set{\beta_{2}}=\beta_{2j}^{j\in J_2}$): $P[Q]_{j_0}	\models \openrule
+\item Finally, for the open transition $\symb{OT}$ in the form ($\set{\beta_{2}}=\beta_{2j}^{j\in J_2}$): $P[Q]_{j_0}	\models \openrule
          {
@@
 By considering $\tau$  actions we split the sequence of actions into $n+1$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.
-We can decompose each of the $n+1$ subsequences;
-
-\includegraphics[width=6cm]{XFIG/proof-explain}
-
-for $k\in [0..n]$ the position of the $k^{\text{th}}$ visible action is  $n_k$, for $k\in [1..n]$,  $n'_k$ is any index between $n_{k-1}$ and $n_k$, additionally $n'_0=0$ and $n'_{n+1}=n_1+n_2+3$.
+We can decompose each of the $n+1$ subsequences; for $k\in [0..n]$ the position of the $k^{\text{th}}$ visible action is  $n_k$, for $k\in [1..n]$,  $n'_k$ is any index between $n_{k-1}$ and $n_k$, additionally $n'_0=0$ and $n'_{n+1}=n_1+n_2+3$.
 We obtain $n+1$ subsequences  made of the following OTs, for all $k\in [0..n]$ :\\
@@
 $\displaystyle{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=\displaystyle{\mybigdotcup_{i=n'_{k}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k}}\!\!\!\Post''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post''_{l}}}} \dotcup\\
-~~\qquad \qquad\qquad\mybigdotcup_{i=n_k+1}^{n'_{k+1}-1}
+~~\qquad \mybigdotcup_{i=n_k+1}^{n'_{k+1}-1}
 \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}} \subst{\bigotimes_{l=i-1}^{n_k\!+\!1}\!\Post''_{l}\shortotimes\Post''_{n_k}\shortotimes\!\!\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post''_{l}} }\\
@@
 
-Note that for all $k\in[0..n-1]$, $v_{kl}'=v_{(k+1)l}$,  $v_{0l}=s_{0l}=s_l$, and $v'_{nl}=v_{(n_1+n_2+3) l}=u_{(n_2+1) l} = s'_l$.
-
-By definition of $\Post_k$, we have $\displaystyle{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j} = \bigotimes_{j=k-1}^{0}\!\!\Post_{j}}$.
+Note that for all $k\in[0..n-1]$, $v_{kl}'=v_{(k+1)l}$, and $v_{0l}=s_{0l}=s_l$ and $v'_{nl}=v_{(n_1+n_2+3) l}=u_{(n_2+1) l} = s'_l$.
+
+By definition of $\Post_k$, we have $\displaystyle{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j} = \bigotimes_{j=k-1}^{0}\!\!\Post_{j}}$
+
 %In this case, the number of weak open transitions
 %might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.\\
-Consequently,  we have:
-\[\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{j}}} =
+Consequently \[\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{j}}} =
 \alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post''_{j}\otimes\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j}}} = \alpha_k'\displaystyle{\subst{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j}}} =
@@
 \bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
-&\iff\bigwedge_{i=0}^{m_1}\left(\Pred'_{1i}
-		\land {\Pred''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}\right)\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}} \\
+&\iff\bigwedge_{i=0}^{m_1}\left(\Pred'_{1p}
+		\land {\Pred''_{1p}}\land \alpha_{1p}=\beta_{1pj_0}\right)\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}} \\
 &\qquad\land\left(\Pred'_{2}
 		\land {\Pred''_{2}}\land \alpha_{2}=\beta_{2j_0}\right)\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
-&\qquad\land\bigwedge_{i=0}^{m_2} \left(\Pred'_{3i}
-		\land {\Pred''_{3i}}\land \alpha_{3i}=\beta_{3ij_0}\right) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
-&\iff\bigwedge_{i=0}^{m_1}\left((\Pred'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}})
-		\land ({\Pred''_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post''_{1j}})\land (\alpha_{1i}=\beta_{1ij_0})\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\right) \\
+&\qquad\land\bigwedge_{i=0}^{m_2} \left(\Pred'_{3p}
+		\land {\Pred''_{3p}}\land \alpha_{3p}=\beta_{3pj_0}\right) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
+&\iff\bigwedge_{i=0}^{m_1}\left((\Pred'_{1p}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}})
+		\land ({\Pred''_{1p}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post''_{1j}})\land (\alpha_{1p}=\beta_{1pj_0})\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\right) \\
 &\qquad\land \left(\Pred'_{2}\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}
 		\land {\Pred''_{2}} \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \land (\alpha_{2}=\beta_{2j_0})\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \right) \\
-&\qquad\land\bigwedge_{i=0}^{m_2} \Bigg(\Pred'_{3i} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} 
-		\land {\Pred''_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}  \\
-		 & \qquad \land (\alpha_{3i}=\beta_{3ij_0}) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\Bigg)  \\
-&\iff \Pred'\land\bigwedge_{k=0}^n\Pred_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}\land\Pred_\beta
-\\&\iff \Pred'\land\bigwedge_{k=0}^n\Pred_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}\land
-(\gamma_{j_0}=[\alpha'_{i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{j}}|i\in[0..n]])
+&\qquad\land\bigwedge_{i=0}^{m_2} \Bigg(\Pred'_{3p} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} 
+		\land {\Pred''_{3p}} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}  \\
+		 & \qquad \land (\alpha_{3p}=\beta_{3pj_0}) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\Bigg)  \\
+&\iff \Pred'\land\bigwedge_{k=0}^n\Pred_k\bigotimes_{j=k-1}^{0}\!\!\Post_{j}\land\Pred_\beta
+\\&\iff \Pred'\land\bigwedge_{k=0}^n\Pred_k\bigotimes_{j=k-1}^{0}\!\!\Post_{j}\land
+(\gamma_{j_0}=[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n]])
 \end{split}\end{equation*}
@@
 P\models\openrule
-         {\beta_2^{j\in J_2},\Pred_2,\Post_2 }
+         {\beta_{2j}^{j\in J_2},\Pred_2,\Post_2 }
          {\ostate{({s_{20i}})^{i\in L}} \OTarrow {\alpha'} \ostate{({s_{21i}})^{i\in L}}}
@@
 \begin{split}
-\Pred&=\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\bigotimes_{j=p-1}^{0}\subst{\Post_{1j}}\big)\land\Pred^2\bigotimes_{p=m_1}^{0}\subst{\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\big(\!\!\bigotimes_{j=p-1}^{0}\subst{\Post_{3j}}\subst{\Post_2}\!\!
-\bigotimes_{p=m_1}^{0}\subst{\Post_{1p}}\big)
+\Pred&=\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\big)\land\Pred^2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}
 \\
-\Post&=\bigotimes_{p=m_2}^{0}\Post_{3p}\subst{\Post_2}\bigotimes_{j=m_1}^{0}\subst{\Post_{1j}}
+\Post&=\bigotimes_{p=m_2}^{0}\Post_{3p}\otimes\Post_2\otimes\bigotimes_{j=m_1}^{0}\Post_{1j}
 \end{split}
@@
 		{
-			\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{1pj}^{j\in J_{1p}\setminus \{j_0\}}}, 
+			\set{\beta'_{1p}}, 
 			\Pred_{1p}\,',  \Post_{1p}\,'
@@
 \begin{mathpar}
-\Pred_{1p}\,'=\Pred_{1p}\land (\beta_{1pj_0}=\alpha_i\land \Pred_i)
+\set{\beta'_{1p}}=\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{1pj}^{j\in J_{1p}\setminus \{j_0\}}}\\
+\Pred\,'_{1p}=\Pred_{1p}\land (\beta_{1pj_0}=\alpha_i\land \Pred_i)
 \\
 %\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
-\Post_{1p}\,'=\Post_{1p}\uplus\Post_i
+\Post\,'_{1p}=\Post_{1p}\uplus\Post_i
 \end{mathpar}
 
-Or $j_0\not \in \dom(\beta_{1 p})$ and $Q$ does not move in the composed reduction
+Or $j_0\not \in \dom(\beta_{1 p})$ and $Q$ does not move in the composed reduction. In this case there is no $i$ such that $p=n_i$, but there is $i$ such that $p\in]n_i .. n_{i+1}[$, and
 \[P[Q]_{j_0} \models\openrule
     {\set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
-         {\ostate{{(s_{1pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s_{1(p+1)i})}^{i\in L}}}
+         {\ostate{s_{1pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTarrow {\tau} \ostate{s_{1(p+1)j}^{j\in L}\uplus s_{ij}^{j\in L_Q}}}
 \]
@@
 \[P[Q]_{j_0} \models\openrule
-    {\set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
-         {\ostate{{(s_{1pi})}^{i\in L}} \OTWeakarrow {\tau} \ostate{{(s_{1(p+1)i})}^{i\in L}}}
+    {\set{\beta'_{1p}},\Pred\,'_{1p},\Post\,'_{1p}   }
+         {\ostate{s_{1pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTWeakarrow {\tau} \ostate{s_{1(p+1)j}^{j\in L}\uplus s_{ij}^{j\in L_Q}}}
 \]
-\item idem for the OT $\alpha$
-\item idem for the last $\tau$s
+with 
+\begin{mathpar}
+\set{\beta'_{1p}}=\set{\beta_{1p}}\\
+\Pred_{1p}\,'=\Pred_{1p}\\
+\Post_{1p}\,'=\Post_{1p}
+\end{mathpar}
+
+\item idem for the middle OT with label $\alpha$:
+\[P[Q]_{j_0}\models\openrule
+         {	\gamma_{m j}^{j\in J_m}\uplus\vis{\beta_{2j}^{j\in J_2\setminus \{j_0\}}},\Pred_2',\Post_2' }
+         {\ostate{{s_{20j}}^{j\in L}\uplus s_{mj}^{j\in L_Q}}\OTarrow {\alpha'} \ostate{{(s_{21j})}^{j\in L}\uplus s_{(m+1)j}^{j\in L_Q}}}\]
+with 
+\begin{mathpar}
+\Pred_{2}\,'=\Pred_{2}\land (\beta_{2j_0}=\alpha_m\land \Pred_m)
+\\
+%\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
+\Post_{2}\,'=\Post_{2}\uplus\Post_m
+\end{mathpar}
+
+\item and for the last $\tau$ OTs:
+for $p\in [0..m_2]$. Either there is $i$ such that $p=n'_i$, and thus $\beta_i=\beta_{1 p j_0}$. In this case by Lemma~\ref{lem-Weakcompose1}, we have:
+
+Then, we have\\[-2ex]
+	\[ P[Q]_{j_0}  
+	\models
+	{\openrule
+		{
+			\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{3pj}^{j\in J_{3p}\setminus \{j_0\}}}, 
+			\Pred_{3p}\,',  \Post_{3p}\,'
+			 }
+		{\ostate{s_{3pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTWeakarrow {\tau}
+			\ostate{s_{3(p+1)j}^{\, j\in L}\uplus s_{(i+1)j}^{j\in L_Q} } }
+	}
+	\]
+with 
+\begin{mathpar}
+\Pred_{3p}\,'=\Pred_{3p}\land (\beta_{3pj_0}=\alpha_i\land \Pred_i)
+\\
+%\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
+\Post_{3p}\,'=\Post_{3p}\uplus\Post_i
+\end{mathpar}
+
+Or $j_0\not \in \dom(\beta_{3 p})$ and $Q$ does not move in the composed reduction. In this case there is no $i$ such that $p=n'_i$, but there is $i$ such that $p\in]n'_i .. n'_{i+1}[$, and
+\[P[Q]_{j_0} \models\openrule
+    {\set{\beta_{3p}},\Pred_{3p},\Post_{3p}   }
+         {\ostate{s_{3pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTarrow {\tau} \ostate{s_{3(p+1)j}^{j\in L}\uplus s_{ij}^{j\in L_Q}}}
+\]
+and thus we also have a weak OT by definition:
+\[P[Q]_{j_0} \models\openrule
+    {\set{\beta_{3p}},\Pred_{3p},\Post_{3p}   }
+         {\ostate{s_{3pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTWeakarrow {\tau} \ostate{s_{3(p+1)j}^{j\in L}\uplus s_{ij}^{j\in L_Q}}}
+\]
+
 \end{enumerate}
 
-What we need here is an adaptation of Lemma~\ref{lem-rel-OT-WOT} where transitions are WOTs and not OTs ... \TODO{I suggest to say that it is a trivial adaptation even if it is not}
+What we need now is an adaptation of Lemma~\ref{lem-rel-OT-WOT} where transitions are WOTs and not OTs ... \TODO{comment depending on the status of lemma 4 bis (Rabea). Thus by Lemma 4 bis:}
+
+However it must be noticed that in steps 1 and 3, we have two kinds of WOTs with different signatures (depending on whether $Q$ moves or not).
+It is still possible to glue them together in a global rules with two more terms for $\Pred$ and $\Post$ terms.
+This global merge is possible because the postconditions of $P$ only act on variables of $P$ and those of $Q$ on variables of $Q$ (for example $\Post_i$ has no effect on $\Pred_{1p}$ and thus does not need to be taken into account when dealing with WOTs where $Q$ does not move).
+We obtain:
+
+	\[ P[Q]_{j_0}  
+	\models
+	{\openrule
+		{
+			\set{\gamma'}, 
+			\Pred\,'',  \Post\,''
+			 }
+		{\ostate{s_{10j}^{j\in L}\uplus s_{0j}^{j\in L_Q}} \OTWeakarrow {\alpha''}
+			\ostate{s_{3(m_2+1)j}^{\, j\in L}\uplus s_{(n+1)j}^{j\in L_Q} } }
+	}
+	\]
+Where\\
+$
+\alpha''=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}\\
+\displaystyle{
+\set{\gamma'}=\mybigdotcup_{i=0}^{m_1} (\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{1pj}^{j\in J_{3p}\setminus \{j_0\}}})\subst{\bigotimes_{j=i-1}^{0} \Post_{1j}' }  
+\dotcup  (\gamma_{m j}^{j\in J_m}\uplus\vis{\beta_{2j}^{j\in J_2\setminus \{j_0\}}})\subst{\bigotimes_{j={m_1}}^{0}\Post_{1j}'}}\\
+\displaystyle{\qquad  \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
+\\
+\Pred=\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=n}^{0}\Post_{1j}}\land\\ 
+~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}}\Big)\\
+\Post=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}
+$
 

### 2019-07-19 2016-Weak-FH-Bisim/WeakBisim.tex

--- 2019-07-19 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 (\alpha'_Q=\beta_{j_0})\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\\
-&=\Pred_Q\land\Pred\land \alpha_Q=\beta_{j_0}
-\end{split}
-\end{equation*}
-\begin{equation*}
-\begin{split}
+&=\Pred_Q\land\Pred\land \alpha_Q=\beta_{j_0}\\
+&\\
 \Post_c&=\Post\uplus\Post_Q

### 2019-07-19 2016-Weak-FH-Bisim/WeakBisim.tex
lemma 7, gamma correction

@@
 $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\
-$\displaystyle{\set{\gamma}=\mybigdotcup_{h=0}^{k} \vis{\set{\beta_{1h}}} \dotcup  \vis{\set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}}}}
+$\displaystyle{
+\set{\gamma}=\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{j=h-1}^{0}\!\! \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=k}^{0}\Post_{1j}}} \dotcup}$\\
+ $~~\hspace{1.8em}\displaystyle{ \mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{j=h-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=k}^{0}\Post_{1j}} }}
 \\
@@
     {
-\set{\gamma'}, \Pred_c,
+\set{\gamma_c}, \Pred_c,
 \Post_c}
@@
 and $\alpha=\alpha'$  because $\Post_{1j}$ acts on variables of $Q$ and $\alpha$ contains only variables of $P$.\\
-
-$\set{\gamma'}=\mybigdotcup_{h=0}^k\vis{\set{\beta_{1h}}} \dotcup \vis{{\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'}\vis{\set{\beta_{3h}}}=\set{\gamma}\uplus\vis{\beta_j^{j\in J\setminus \{j_0\}}}$\\
-$\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_i{1i}}\land
+$\displaystyle{
+\set{\gamma_c}=\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{i=h-1}^{0}\!\!
+\Post_{1i} } }  \dotcup  \vis{({\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2})\subst{\bigotimes_{i=k}^{0}\Post_{1i}}} \dotcup}$ \\
+$~~\hspace{1.8em}\displaystyle{\mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{i=h-1}^{0}\!\!\Post_{3i}\shortotimes\Post_2\shortotimes\bigotimes_{i=k}^{0}\Post_{1i}} }}$\\
+$~~\hspace{0.6em}=\set{\gamma}\uplus\vis{\beta_j^{\in J\setminus \{j_0\}}} \quad$  because $\Post_{1j}$  does not act on variables of $\beta_j$.  \\
+$\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_{1i}}\land
 \left(Pred\land\Pred_2\land \alpha'_Q=\beta_{j_0 }\right)\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land\\\displaystyle

### 2019-07-25 2016-Weak-FH-Bisim/WeakBisim.tex
Proof of lemma 8 !

@@
 such that\\ 
-$\alpha_Q=\alpha'_Q\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$\\
+{\footnotesize $\alpha_Q=\alpha'_Q\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$\\
 $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\
@@
 $
-
+}
 \begin{enumerate}
@@
 and $\alpha=\alpha'$  because $\Post_{1j}$ acts on variables of $Q$ and $\alpha$ contains only variables of $P$.\\
-$\displaystyle{
+{\footnotesize $\displaystyle{
 \set{\gamma_c}=\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{i=h-1}^{0}\!\!
@@
 $\Post_c=\displaystyle{(\bigotimes_{i=k'}^{0}{\Post_{3i}})\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}$
-
+}
 Note that we have $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\
@@
 \\
-\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
+\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}\subst{\bigotimes_{k=t}^{0}{\Post_k}}}\text{\quad and\quad}
 \Post\,'=\Post\uplus\bigotimes_{t=n}^{0}
@@
 \end{mathpar}
-\TODO{add posts to gammaj's above}
 Then, we have\\[-2ex]
@@
 By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
-$\forall p\!\in\![0..m_1].P\models\openrule
+\begin{mathpar}
+\forall p\!\in\![0..m_1].P\models\openrule
     {{\beta_{1pj}^{j\in J_{1p}}},\Pred_{1p},\Post_{1p}   }
-         {\ostate{{(s_{1pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s_{1(p+1)i})}^{i\in L}}} \wedge
+         {\ostate{{(s_{1pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s_{1(p+1)i})}^{i\in L}}} \\
 P\models\openrule
@@
          {\ostate{({s_{20i}})^{i\in L}} \OTarrow {\alpha'} \ostate{({s_{21i}})^{i\in L}}}
-\wedge\\
+\\
 \forall p \in [0..m_2].P\models\openrule
@@
            \beta_{3pj}^{j\in J_{3p}},\Pred_{3p}, \Post_{3p}}
-         { \ostate{(s_{3pi})^{i\in L}} \OTarrow {\tau} \ostate{(s_{3(p+1)i})^{i\in L}}}$ 
-\\
+         { \ostate{(s_{3pi})^{i\in L}} \OTarrow {\tau} \ostate{(s_{3(p+1)i})^{i\in L}}}
+\end{mathpar}
 where for all $i\in L$:\\
@@
 \[\alpha=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}}\]
-\[\displaystyle{
-\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{1p}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\Post_{1j}}}}\]
+\begin{multline*}
+\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \\
+\dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{1p}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\Post_{1j}}}
+\end{multline*}
+\begin{multline*}
+\Pred=\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\big)\land\Pred^2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\ \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}
+\end{multline*}
 \begin{equation*}
 \begin{split}
-\Pred&=\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\big)\land\Pred^2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}
-\\
 \Post&=\bigotimes_{p=m_2}^{0}\Post_{3p}\otimes\Post_2\otimes\bigotimes_{j=m_1}^{0}\Post_{1j}
@@
 \begin{split}
-\forall{i\in[0..m-1]}.],&\beta_{1 n_i j_0}\subst{\bigotimes_{j=n_i-1}^{0} \Post_{1j} }=\beta_i\\ 
+\forall{i\in[0..m-1]},&\beta_{1 n_i j_0}\subst{\bigotimes_{j=n_i-1}^{0} \Post_{1j} }=\beta_i\\ 
 &
 \beta_{2 j_0}\subst{\bigotimes_{j=m_1}^{0} \Post_{1j} }=\beta_m\\ 
-\forall{i\in[m+1..n]}.],&\beta_{3 n'_i j_0}\subst{\bigotimes_{j=n'i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\Post_{1j}}=\beta_i\\ 
+\forall{i\in[m+1..n]},&\beta_{3 n'_i j_0}\subst{\bigotimes_{j=n'i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\Post_{1j}}=\beta_i\\ 
 \end{split}\end{equation*}
@@
 \begin{enumerate}
-\item $p\in [0..m_1]$. Either there is $i$ such that $p=n_i$, and thus $\beta_i=\beta_{1 p j_0}$. In this case by Lemma~\ref{lem-Weakcompose1}, we have:
+\item $p\in [0..m_1]$. Either there is $i$ such that $p=n_i$, and thus $\beta_i$ and $\beta_{1 p j_0}$ are defined. In this case by Lemma~\ref{lem-Weakcompose1}, we have:
 
@@
 		{
-			\set{\beta'_{1p}}, 
+			\set{\gamma'_{1p}}, 
 			\Pred_{1p}\,',  \Post_{1p}\,'
@@
 \begin{mathpar}
-\set{\beta'_{1p}}=\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{1pj}^{j\in J_{1p}\setminus \{j_0\}}}\\
+\set{\gamma'_{1p}}=\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{1pj}^{j\in J_{1p}\setminus \{j_0\}}}\\
 \Pred\,'_{1p}=\Pred_{1p}\land (\beta_{1pj_0}=\alpha_i\land \Pred_i)
@@
 \[P[Q]_{j_0} \models\openrule
-    {\set{\beta'_{1p}},\Pred\,'_{1p},\Post\,'_{1p}   }
+    {\set{\gamma'_{1p}},\Pred\,'_{1p},\Post\,'_{1p}   }
          {\ostate{s_{1pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTWeakarrow {\tau} \ostate{s_{1(p+1)j}^{j\in L}\uplus s_{ij}^{j\in L_Q}}}
@@
 \begin{mathpar}
-\set{\beta'_{1p}}=\set{\beta_{1p}}\\
-\Pred_{1p}\,'=\Pred_{1p}\\
-\Post_{1p}\,'=\Post_{1p}
+\set{\gamma'_{1p}}=\set{\vis{\beta_{1p}}}\\
+\Pred\,'_{1p}=\Pred_{1p}\\
+\Post\,'_{1p}=\Post_{1p}
 \end{mathpar}
@@
 \[P[Q]_{j_0}\models\openrule
-         {	\gamma_{m j}^{j\in J_m}\uplus\vis{\beta_{2j}^{j\in J_2\setminus \{j_0\}}},\Pred_2',\Post_2' }
-         {\ostate{{s_{20j}}^{j\in L}\uplus s_{mj}^{j\in L_Q}}\OTarrow {\alpha'} \ostate{{(s_{21j})}^{j\in L}\uplus s_{(m+1)j}^{j\in L_Q}}}\]
+         {	\set{\gamma'_2},\Pred_2',\Post_2' }
+         {\ostate{{s_{20j}}^{j\in L}\uplus s_{mj}^{j\in L_Q}}\OTWeakarrow {\alpha'} \ostate{{(s_{21j})}^{j\in L}\uplus s_{(m+1)j}^{j\in L_Q}}}\]
 with 
 \begin{mathpar}
-\Pred_{2}\,'=\Pred_{2}\land (\beta_{2j_0}=\alpha_m\land \Pred_m)
+\set{\gamma'_2}=\gamma_{m j}^{j\in J_m}\uplus\vis{\beta_{2j}^{j\in J_2\setminus \{j_0\}}}\\
+\Pred\,'_{2}=\Pred_{2}\land (\beta_{2j_0}=\alpha_m\land \Pred_m)
 \\
 %\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
-\Post_{2}\,'=\Post_{2}\uplus\Post_m
+\Post\,'_{2}=\Post_{2}\uplus\Post_m
 \end{mathpar}
@@
 \item and for the last $\tau$ OTs:
-for $p\in [0..m_2]$. Either there is $i$ such that $p=n'_i$, and thus $\beta_i=\beta_{1 p j_0}$. In this case by Lemma~\ref{lem-Weakcompose1}, we have:
+for $p\in [0..m_2]$. Either there is $i$ such that $p=n'_i$, and thus $\beta_i$ and $\beta_{1 p j_0}$ are defined. In this case by Lemma~\ref{lem-Weakcompose1}, we have:
 
@@
 		{
-			\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{3pj}^{j\in J_{3p}\setminus \{j_0\}}}, 
-			\Pred_{3p}\,',  \Post_{3p}\,'
+			\set{\gamma'_{3p}}, 
+			\Pred\,'_{3p} ,  \Post\,'_{3p} 
 			 }
@@
 \begin{mathpar}
-\Pred_{3p}\,'=\Pred_{3p}\land (\beta_{3pj_0}=\alpha_i\land \Pred_i)
+\set{\gamma'_{3p}}=\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{3pj}^{j\in J_{3p}\setminus \{j_0\}}}\\
+\Pred\,'_{3p}=\Pred_{3p}\land (\beta_{3pj_0}=\alpha_i\land \Pred_i)
 \\
 %\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
-\Post_{3p}\,'=\Post_{3p}\uplus\Post_i
+\Post\,'_{3p} =\Post_{3p}\uplus\Post_i
 \end{mathpar}
@@
 \[P[Q]_{j_0} \models\openrule
-    {\set{\beta_{3p}},\Pred_{3p},\Post_{3p}   }
+    {\set{\gamma'_{3p}},\Pred\,'_{3p},\Post\,'_{3p}   }
          {\ostate{s_{3pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTWeakarrow {\tau} \ostate{s_{3(p+1)j}^{j\in L}\uplus s_{ij}^{j\in L_Q}}}
 \]
+with 
+\begin{mathpar}
+\set{\gamma'_{3p}}=\set{\beta_{3p}}\\
+\Pred\,'_{3p} =\Pred_{3p}\\
+\Post\,'_{3p} =\Post_{3p}
+\end{mathpar}
 
@@
 What we need now is an adaptation of Lemma~\ref{lem-rel-OT-WOT} where transitions are WOTs and not OTs ... \TODO{comment depending on the status of lemma 4 bis (Rabea). Thus by Lemma 4 bis:}
-
-However it must be noticed that in steps 1 and 3, we have two kinds of WOTs with different signatures (depending on whether $Q$ moves or not).
-It is still possible to glue them together in a global rules with two more terms for $\Pred$ and $\Post$ terms.
-This global merge is possible because the postconditions of $P$ only act on variables of $P$ and those of $Q$ on variables of $Q$ (for example $\Post_i$ has no effect on $\Pred_{1p}$ and thus does not need to be taken into account when dealing with WOTs where $Q$ does not move).
  We obtain:
@@
 \displaystyle{
-\set{\gamma'}=\mybigdotcup_{i=0}^{m_1} (\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{1pj}^{j\in J_{3p}\setminus \{j_0\}}})\subst{\bigotimes_{j=i-1}^{0} \Post_{1j}' }  
-\dotcup  (\gamma_{m j}^{j\in J_m}\uplus\vis{\beta_{2j}^{j\in J_2\setminus \{j_0\}}})\subst{\bigotimes_{j={m_1}}^{0}\Post_{1j}'}}\\
-\displaystyle{\qquad  \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
+\set{\gamma'}=
+ \mybigdotcup_{i=0}^{m_1}\set{\gamma'_{1i}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{1k}}\dotcup
+ \set{\gamma'_{2}}\subst{\bigotimes_{k=m_1}^{0}\Post\,'_{1k}}\dotcup
+ \mybigdotcup_{i=0}^{m_2}\set{\gamma'_{3i}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}
+}
 \\
-\Pred=\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=n}^{0}\Post_{1j}}\land\\ 
-~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}}\Big)\\
-\Post=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}
+%\mybigdotcup_{i=0}^{m_1} (\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{1pj}^{j\in J_{3p}\setminus \{j_0\}}})\subst{\bigotimes_{j=i-1}^{0} \Post_{1j}' }  
+%\dotcup  (\gamma_{m j}^{j\in J_m}\uplus\vis{\beta_{2j}^{j\in J_2\setminus \{j_0\}}})\subst{\bigotimes_{j={m_1}}^{0}\Post_{1j}'}}\\
+%\displaystyle{\qquad  \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
+%\\
+\Pred\,''=\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\ 
+~\qquad\quad\Big(\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_2}^{0}\Post\,'_{1j}}\Big)\\
+\Post\,''=\bigotimes_{j=m_2}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}
 $
 
-\TODO{I think the rest is useless (old proof sketch)}
-
-Moreover, we have for all $t\in[0..n]$:
-\begin{mathpar}
-Q\models{\openrule
-	{
-		\gamma_{t j}^{j\in J_t},
-		 \Pred_t,  
-		\Post_t}
-	{\ostate{s_{t i}^{i\in L_Q}} \OTWeakarrow {\alpha_t}
-		\ostate{s_{(t+1) i}^{\, i\in L_Q}}}
-}		
-\end{mathpar}
-%In the same way,  by Lemma \ref{lem-rel-OT-WOT} we can decompose $\WOT_p$ into  a series of $m'+n'$ tau open transitions and a single observable open transition:
-%\[Q\models{\openrule
-%			{
-%				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred'^{2}}},  
-%				{{\Post'^{2}}}}
-%				{\ostate{s_{p i}^{i\in L_Q}} \OTarrow {\alpha_p}
-%				\ostate{s_{(p+1) i}^{i\in L_Q}}}
-%				}%\]
-%\]
-
-We proceed by iteration on the list of  OTs of $P$ identified above, these OTs are of the form, for $l\in\{1,2,3\}$: 
-\[P\!\models		
-\openrule
-    {
-       {(\beta^l_{p j})^{j\in J}},\Pred_p,\Post_p   }
-         {\ostate{s^{i\in L}_{pi}} \OTarrow {\alpha^l} \ostate{s^{i\in L}_{(p+1)i}}}\]
-with $\alpha^2=\alpha$ and $\alpha^1=\alpha^3=\tau$
-
-We use an additional variable $t$, in the iteration, it will be used as an index from $0$ to $n$, i.e. inside the OTs of $Q$.
-At the beginning $t=0$, i.e. $Q$ is at state $\ostate{s_{0}}$. \TODO{on peut remplacer $s_t$ par $s_{t i}^{i\in L_Q}$}
-For each step of the iteration, we have two cases:
-\begin{itemize}
-\item If $j_0\in J$ then Q moves by one open transition. By the hypothesis above $\beta^i_{p j_0}\neq \tau$. Additionally, we have 
-$\displaystyle{\gamma_j^{j\in J}=\mybigdotcup_{p=0}^{m_1} \vis{\set{\beta^1_p}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{p=0}^{m_2} \vis{\set{\beta^3_p}}}$ and\\
- $\gamma_{j_0}=[\beta_0..\beta_n]$, thus
-  $\beta^i_{p j_0}=\beta_t$ with  for some $t$ such that $t$ has value $0$ at beginning and that is incremented whenever this condition is satisfied.
-
-On the other hand, by hypothesis we have \TODO{on peut remplacer $s_t$ par $s_{t i}^{i\in L_Q}$}:
-\[Q\models{\openrule
-	{
-		\gamma_{t j}^{j\in J_t},
-		 \Pred_t,  
-		\Post_t}
-	{ \ostate{s_{t}}\OTWeakarrow {\alpha_t}
-		\ostate{s_{{(t+1)}}}}
-}
-\]
-By  Lemma \ref{lem-rel-OT-WOT} we can decompose this $\WOT$ into  a series of $k+1$ and $k'+1$ tau open transitions and an observable open transition:
-
-\[\forall h\!\in\![0..k].Q\models\openrule
-    {\set{\beta^1_h},\Pred^1_h,\Post^1_h   }
-         {\ostate{{(s^1_{h})}} \OTarrow {\tau} \ostate{{(s^1_{(h+1)})}}}
-\]
-
-\[Q\models{\openrule
-	{
-		\set{\beta^2},
-		 \Pred^2,  
-		\Post^2}
-	{\ostate{s^2_{0}}\OTarrow {\alpha_t}
-		\ostate{s^2_{1}}}
-}
-\]
-
-\[
-\forall h \in [0..k'].Q\models\openrule
-         {
-           \set{\beta^3_h},\Pred^3_h, \Post^3_h}
-         { \ostate{(s^3_h)} \OTarrow {\tau} \ostate{(s^3_{(h+1)})}} \]
-
-such that 
-$s_t=s^1_{0} \wedge s^1_{(k+1) i}=s^2_{0} \wedge  s^2_{1}= s^3_{0} \wedge s^3_{(k'+1) i}=s_{t+1}$\\
-
-$\displaystyle{\gamma_{t j}^{j\in J_t}=\mybigdotcup_{h=0}^{k} \vis{\set{\beta^1_h}} \dotcup  \vis{\set{\beta^2}} \dotcup \mybigdotcup_{h=0}^{k'} \vis{\set{\beta^3_h}}}\\
-\Pred_t=\bigwedge_{h=0}^{k}\!\big(\Pred^1_h\bigotimes_{j=h-1}^{0}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{h=k}^{0}\subst{\Post_h^1}\land \bigwedge_{h=0}^{k'}\!\Pred_h^3\big(\bigotimes_{j=h-1}^{0}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{h=k}^{0}\subst{\Post_h^1}\big)\\
-\Post=\bigotimes_{h=k'}^{0}\Post^3_h\subst{\Post^2}\bigotimes_{j=k}^{0}\subst{\Post^1_j}
-$
-
-\begin{enumerate}
-
-\item For the first $k$ open tau transitions, by Definition \ref{def:Non-ObsTau} $P$ can necessarily make a tau open transition if the hole indexed $j_0$ makes a tau action.
-So by Lemma \ref{lem-compose} we obtain $k$ open transitions in the form: \TODO{remarquer la notation compliquee ou trouver une meilleure notation mais pas trop lourde}
-\[P[Q]_{j_0}\!\models		
-\openrule
-    {
-       \set{\beta^1_h},{\Pred^1_h},{\Post^1_h}   }
-         {\ostate{s^1_h\uplus s^{i\in L}_{pi} } \OTarrow {\tau} \ostate{s^1_{h+1}\uplus s^{i\in L}_{pi}}}\]
-
-\item For the observable open transition.  By Lemma \ref{lem-compose} we obtain:\\ 
-	\[ P[Q]_{j_0}  
-	\models
-	{\openrule
-		{
-			{\beta^i_{p j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}, 
-			\Pred_p\land\Pred^2\land \alpha_t=\beta^i_{p j_0 },  
-			\Post_p\uplus \Post^2}
-{\ostate{s^{i\in L}_{pi}\uplus s_0^2} \OTarrow {\alpha_p} \ostate{s^{i\in L}_{(p+1)i}\uplus s_1^2}}
-	}
-	\]
-
-%
-%\[P[Q]_{j_0}\!\models		
-%\openrule
-%    {
-%       {\beta^i_{p j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2},{\Pred_p}\!\!'',{\Post_p}\!\!''   }
-%         {\ostate{s^{i\in L \uplus L_Q}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L\uplus L_Q }_{(p+1)i}}}\] \\
-% such that  ${\Pred_p}\!\!'' \iff {\Pred_p}
-%		\land {\Pred_p}\!\!'\land \alpha_t=\beta_{j_0}$, ${\Post_p}\!\!''={\Post_p}\uplus 
-%		{\Post_p}\!\!'$\\ 
-\item We proceed in the same way as the first item for $k'$ last weak open transitions, and we obtain $k'$ open tau transitions.\\
-\end{enumerate}
-
-By Lemma \ref{lem-rel-OT-WOT} from cases $(1)$, $2$ and $(3)$ we obtain: 
-\[P[Q]_{j_0}\!\models		
-\openrule
-    {
-\set{\gamma}, \Pred_c,
-\Post_c}
-         {\ostate{s^1_0\uplus s^{i\in L}_{pi}} \OTWeakarrow {\alpha^l} 
-	\ostate{{s^{i\in L}_{(p+1)i}\uplus s_{k'}^3}}}\] 
-where
-\[\set\gamma=\mybigdotcup_{h=0}^k\vis{\set{\beta^1_h}} \dotcup \vis{{\beta^i_{p j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}} \dotcup \mybigdotcup_{h=0}^{k'}\vis{\set{\beta^3_h}}\]
-\[
-\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred^1_h}\subst{\bigotimes_{i=h-1}^{0}\Post_i^1}\land
-\left(Pred_p\land\Pred^2\land \alpha_t=\beta^i_{p j_0 }\right)\subst{\bigotimes_{i=k}^{0}{\Post_i^1}}\land\\\displaystyle
-\bigwedge_{h=0}^{k'}{\Pred^3_h}\subst{\bigotimes_{i=h-1}^{0}{\Post_i^3}\shortotimes({\Post_p\uplus \Post^2})\shortotimes\bigotimes_{i=k}^{0}{\Post_i^1}}
-\end{array}
-\]
-
-\[\Post_c=(\bigotimes_{i=k'}^{0}{\Post_i^3})\shortotimes({\Post_p\uplus \Post^2})\shortotimes\bigotimes_{i=k}^{0}{\Post_i^1}
-\]
-Note that we have $s_t=s^1_{0} \wedge s^1_{(k+1) i}=s^2_{0} \wedge  s^2_{1}= s^3_{0} \wedge s^3_{(k'+1) i}=s_{t+1}$
-
- \item Else, $j_0\not\in J$. $t$ does not move  and $Q$ does not move, i.e. we have: $\ostate{(s_{t})} = \ostate{({s}_{(t+1)})}$
-By lemma~\ref{lem-compose-2} we have:
-\[P[Q]_{j_0}\!\models		
-\openrule
-    {
-       {(\beta^l_{p j})^{j\in J}},\Pred_p,\Post_p   }
-         {\ostate{s^{i\in L}_{pi}\uplus s_t} \OTarrow {\alpha^l} \ostate{s^{i\in L}_{(p+1)i}\uplus s_t}}
-\]
-and thus
-\[P[Q]_{j_0}\!\models		
-\openrule
-    {
-       \vis{{(\beta^l_{p j})^{j\in J}}},\Pred_p,\Post_p   }
-         {\ostate{s^{i\in L}_{pi}\uplus s_t} \OTWeakarrow {\alpha^l} \ostate{s^{i\in L}_{(p+1)i}\uplus s_t}}
-\]
-
-\end{itemize}
-
----------------------------------------------------------
-
-au depart sQ0
-
-pour chaque etape de P
-- si $j_0\in J$ alors on fait une transition de Q, par definition $\beta^i_{j_0}=\beta_t$ with $\beta^i_{j_0}\neq \tau$ pour un certain t (t vaut 0 au debut et est incremente a chaque fois qu on passe dans cette condition).
-Dans ce cas, Q est dans l etat $s_{t Q}$ avec au depart $s_{0 Q}$ qui est l etat initial de Q avant la premiere OT de Q
-
-(t et p c est un peu la meme chose)
-
-donc on peut faire la transition numero t de Q (WOT)
- on la decompose by Lemma \ref{lem-rel-OT-WOT}
-on a une famille d'OT
-
-k $\tau$
-$s'_h \OTarrow {\tau} s'_{h+1}$
-
-\[Q\models{\openrule
-			{
-				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred'^{2}}},  
-				{{\Post'^{2}}}}
-				{\ostate{s_{i}^{i\in L_Q}} \OTarrow {\alpha_p}
-				\ostate{s_{i}'^{i\in L_Q}}}
-				}%\]
-\]
-
-k' $\tau$
-$s''_h \OTarrow {\tau} s''_{h+1}$
-
-On commence par les $k$ premiers $\tau$
-On applique Def 11 pour dire que 
-P peut faire des transitions ou l etat de P ne bouge pas et le trou $j_0$ fait tau (le reste ne fait rien).
-Par le lemme 2 on compose P qui laisse passer un tau et Q qui fait tau on obtient une OT tau de P[Q].
-Finalement l'etat de Q atteint $s'_k$ avec
-$s'_k = \ostate{s_{i}^{i\in L_Q}}$. (A)
-
-La on peut faire l'OT  $\OTarrow {\alpha_p}$
-par le lemme 2 on compose les OT $\OTarrow {\alpha_p}$ et $\OTarrow {\alpha}$ on obtient un OT $\alpha$ pour P[Q] avec la condition $\alpha_p=\beta_{j_0}$ (dans le Pred du lemma 2). (B)
-
-On termine par les $k'$ derniers $\tau$
-On applique Def 11 et le lemme 2 comme au dessus pour dire que 
-P[Q] peut faire des OT tau ou l etat de P ne bouge pas et l'etat de Q atteint $s''_{k'}$ avec
-${s''}_{k'} = \ostate{(s'_{i})^{i\in L_Q}}$. (C)
-
-en composant (A) (B) et (C) on obtient une WOT k tau, 1 aplha et k' tau pour le pNet P[Q]
-
-$t$ incremente et $s_t$ devient $\ostate{(s'_{i})^{i\in L_Q}}$
-
-- sinon $j_0\not\in J$ : t ne bouge pas, l'etat de Q ne bouge pas (Q ne fait rien) on a la meme OT pour P[Q] que pour P
-
-\begin{enumerate}
-\item
-
- If $Q$ moves meaning that we have $Q\!\models		
-\openrule
-    {
-       {\beta_p^{p\in J_Q}},{\Pred_p}\!\!',{\Post_p} \!\!'  }
-         {\ostate{s^{i\in L}_{pi}} \OTarrow {\alpha_p'} \ostate{s^{i\in L}_{(p+1)i}}}$ and having that there exists $j_0\in J$ such that $\alpha'_p=\beta_{j_0}$ then  by Lemma \ref{lem-compose} we obtain:\\
-\[P[Q]_{j_0}\!\models		
-\openrule
-    {
-       \beta_p^{(p\in J\setminus\{j_0\}) \uplus J_Q},{\Pred_p}\!\!'',{\Post_p}\!\!''   }
-         {\ostate{s^{i\in L \uplus L_Q}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L\uplus L_Q }_{(p+1)i}}}\] \\
- such that  ${\Pred_p}\!\!'' \iff {\Pred_p}
-		\land {\Pred_p}\!\!'\land \alpha_p'=\beta_{j_0}$, ${\Post_p}\!\!''={\Post_p}\uplus 
-		{\Post_p}\!\!'$ 
-		\item Else $Q$ does not move, i.e. we have: $\ostate{(s_{pi})^{i\in L_Q}} = \ostate{({s}_{(p+1)i})^{i\in L_Q}}$. By Definition \ref{def:Non-ObsTau} we write:
-
-		\[ Q\!\models \openrule
-         {
-           (j\mapsto\tau),\True,\Id(s_{pi})}
-         { \ostate{s^{i\in L}_{pi}} \OTarrow {\tau}\ostate{s^{i\in L}_{pi}}}\]
-So we obtain by Lemma \ref{lem-compose}:
-\[P[Q]_{j_0}\!\models		
-\openrule
-    {
-       \beta_p^{(p\in J\setminus\{j_0\}) \uplus J_Q},{\Pred_p}\!\!',  {\Post_p}\!\!' }
-         {\ostate{s^{i\in L\uplus L_Q}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L\uplus L_Q}_{(p+1)i}}}\] \\
-\end{enumerate}
-Therefore we  obtain a series of $m+n$ tau open transitions and a single observable open transition. Thus by Lemma \ref{lem-rel-OT-WOT} that implies we have:
-\[P[Q]_{j_0}\!\models		
-\openrule
-    {
-       \beta_p^{(p\in J\setminus\{j_0\}) \uplus J_Q}, {\Pred_p}
-		\land {\Pred_p}\!\!'\land \alpha_p'=\beta_{j_0}$, ${\Post_p}\!\!''={\Post_p}\uplus 
-		{\Post_p}\!\!'}
-         {\ostate{s^{i\in L\uplus L_Q}_{pi}} \OTWeakarrow {\alpha} \ostate{s^{i\in L \uplus L_Q}_{(p+1)i}}}\] 
-\qed
+However it must be noticed that in steps 1 and 3, we have two kinds of WOTs with different signatures (depending on whether $Q$ moves or not).
+It is still possible to glue them together in a global rules with two more terms for $\Pred$ and $\Post$ terms.
+This global merge is possible because the postconditions of $P$ only act on variables of $P$ and those of $Q$ on variables of $Q$ (for example $\Post_i$ has no effect on $\Pred_{1p}$ and thus does not need to be taken into account when dealing with WOTs where $Q$ does not move).
+
+We now have to compare each element of the obtained WOT with the conclusion of the lemma:
+\begin{align*}
+\alpha''&=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}\\
+& = \alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}}&\text{$\alpha'$ only contains variables of $P$ untouched by $\Post_i$}\\
+& = \alpha
+\end{align*}
+
+For $\set{\gamma'}$ we distinguish elements in the holes of $P$ and of $Q$.
+First suppose $j\in J\setminus\{j_0\}$ we have $\gamma'_j=\gamma_j$ because $\Post'_{ij}$ has no effect on variables of $P$ and on $\beta_{1pj}$, consequently
+\begin{multline*}
+\gamma'_j=\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \dotcup  \vis{{\beta_{2j}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}} \\
+\dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}
+\end{multline*}
+Now, when $j\in J_t$ for some $t$,  $\gamma'_j$ is the concatenation of elements of $\gamma'_{1ij}$, $\gamma_2'$, $\gamma'_{3ij}$  that are not empty.
+By construction the concatenation of these elements is $\gamma_{tj}$, for $t\in[0..n]$.
+$\Post_{ik}$ has no effect on $\gamma_{tj}$ but  $\Post_{k}$ has \TODO{do we want to be more explicit in the explanation?
+giving the exact indices is cumbersome because Post'ij is either empty or postij for the same indices as gamma, this can also be related with the ni and n'i}:
+\begin{align*}
+\gamma'_j&=
+\mybigdotcup_{i=0}^{m_1}\set{\gamma'_{1i}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{1k}}\dotcup
+ \set{\gamma'_{2}}\subst{\bigotimes_{k=m_1}^{0}\Post\,'_{1k}}\dotcup
+ \mybigdotcup_{i=0}^{m_2}\set{\gamma'_{3i}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}\\
+&=
+\mybigdotcup_{t=0}^{n} {\gamma_{tj}}\subst{\bigotimes_{k=t-1}^{0} \Post_{k} }   
+\end{align*}
+
+Concerning predicates, we also separate predicates on $P$ from predicates on $Q$, and from the equality on the action filling the hole:
+{\footnotesize \begin{equation*}
+\begin{split}
+\Pred''&=\Big(\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\ &\qquad
+~\quad\bigwedge_{i=0}^{m_3}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\Big)\\
+&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\land\Pred^2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\&\qquad \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\Big)\\&\qquad
+\land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i\\&\qquad
+\land \Big( \bigwedge_{i=0}^{m-1}(\beta_{1{n_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j={n_i}-1}^{0}\Post\,'_{1j}}\land(\beta_{2{j_0}}=\alpha_m) \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\ &\qquad
+~\quad\bigwedge_{i=m+1}^{n}(\beta_{3{n'_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j=n'_i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\Big)\\
+&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\big)\land\Pred^2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\&\qquad \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\Big)\\&\qquad
+\land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i\\&\qquad
+\land \Big(\bigwedge_{i=0}^{m-1}(\beta_{i}=\alpha_i)\subst{\bigotimes_{j={i-1}}^{0}\Post_{j}}\land(\beta_m=\alpha_m )\subst{\bigotimes_{j=m}^{0}\Post_{j}}\land\\ &\qquad
+~\quad\bigwedge_{i=m+1}^{n}(\beta_i=\alpha_i)\subst{\bigotimes_{j=i-1}^{m}\Post_j\shortotimes\Post_m\shortotimes\bigotimes_{j=m-1}^{0}\Post_{j}}\Big)\\
+&=\Pred
+\end{split}
+\end{equation*}
+}
+
+Finally, concerning postconditions:
+{\footnotesize \begin{equation*}
+\begin{split}
+\Post\,''&=\bigotimes_{j=m_2}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}\\
+&=\left(\bigotimes_{j=m_2}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}\right)\uplus \bigotimes_{j=n}^{0}\Post_j\\
+&=\Post \uplus \bigotimes_{j=n}^{0}\Post_j\
+\end{split}
+\end{equation*}
+}
+This allows us to conclude concerning the lemma. \qed
 \end{proof}

### 2019-09-02 2016-Weak-FH-Bisim/WeakBisim.tex
suppress old proof

@@
 
-What we need now is an adaptation of Lemma~\ref{lem-rel-OT-WOT} where transitions are WOTs and not OTs ... \TODO{comment depending on the status of lemma 4 bis (Rabea). Thus by Lemma 4 bis:}
- We obtain:
+By definition of weak open transition (Definition~\ref{def:buildweakOT}),
+ we obtain:
 
@@
 \newpage
-
-\TODO{Anciennement debut preuve equivalnec weak FH-bisimulation}
-
-Consider 3 open automata 
-       	$\mathcal{T}_1$, $\mathcal{T}_2$, $\mathcal{T}_3$ and states $s$, $t$, $u$ 
-       	in those 
-       	automata\footnote{We omit the constraints stating that each $s_x,\,t_x,\,u_x$ is 
-       	in the 
-       	states of 
-       		$\mathcal{T}_1,\,\mathcal{T}_2,\,\mathcal{T}_3$ for the sake of readability}.
-       	Suppose we have $\mathcal{R}$ an FH-bisimulation relation between states of 
-       	$\mathcal{T}_1$ and of  $\mathcal{T}_2$; members of $\mathcal{R}$ are of the form 
-       	$(s,t|\Pred_{s,t})$.
-       	Suppose we also  have $\mathcal{R}'$ an FH-bisimulation relation between states 
-       	of 
-       	$\mathcal{T}_2$ and of  $\mathcal{T}_3$; members of $\mathcal{R}'$ are of the 
-       	form 
-       	$(t,u|\Pred_{t,u})$.
-
-       	Let $\mathcal{R}''$ be the relation: 
-       	\[\mathcal{R}'' = 
-       	\{(s,u|\Pred_{s,u})\,\,\Big|\,\Pred_{s,u}=\bigvee_{\begin{array}{c}       		
-       		(s,t|\Pred_{s,t})\in\mathcal{R}\\ (t,u|\Pred_{t,u})\in\mathcal{R}' 	
-       		\end{array}
-       	}\,\Pred_{s,t}\land\Pred_{t,u}\}\]
-
-This relation is the adaptation of the transitivity to the conditional relationship that 
-defines a bisimulation. Indeed the global disjunction together with the conjunction of 
-predicates plays exactly the role of the intermediate element in a transitivity rule: 
-``there exists an intermediate state'' corresponds to the global disjunction, and the 
-conjunction of states expresses the intermediate predicate is used to ensure 
-satisfiability of the predicate relating the first state to the last one.
-
-       	The relation is built as follows: for each pair of states $s$, $u$, for each 
-       	state 
-       	$t$ such that $\mathcal{R}$ relates $s$ and $t$, and $\mathcal{R}'$ relates 
-       	$t$ 
-       	and $u$, we take the conjunction of the two predicates. The predicates for 
-       	different 
-       	values of $t$ are collected by a disjunction.
-
-       	We will show
-       	that $\mathcal{R}''$ is an FH-bisimulation. Consider 
-       	$(s,u|\Pred_{s,u})\in\mathcal{R}''$. Then there is a set of states of 
-       	$\mathcal{T}_2$ relating $s$ and $u$, let $(t_p)^{p\in P}$ be this family.  
-       	       	We have $\Pred_{s,u} = \bigvee_{p\in P} \Pred_{s,p}\land\Pred_{p,u}$.
-
-\medskip
-
-       	For any $p\in P$ by definition of $\mathcal{R}''$,
-       	$(s,t_p|\Pred_{s,p})\in\mathcal{R}$,  and 
-       	$(t_p,u|\Pred\,'_{p,u})\in\mathcal{R}'$. 
-       	We have 
-       	the 
-       	following by definition of bisimulation:
-For any $p\in \mathcal{S}_2$ by definition of $\mathcal{R}''$, $(s,p|\Pred_{s,p})\in\mathcal{R}$,  and $(p,u|\Pred_{p,u})\in\mathcal{R}'$. 
-We have the following by definition of weak bisimulation:\\
-For any open transition $OT$ in $\mathcal{T}_1$ originating from $s$.
-       	\begin{mathpar}
-       	\openrule
-       	{
-       		\beta_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
-       	{s \OTarrow {\alpha} {s}'}  \qquad (1)   	
-       	\end{mathpar}
-
-       	There exist weak open transitions $OT_{px}^{x\in X} \subseteq \mathcal{T}_2$:
-
-       	\begin{mathpar} 
-       	%    \left( fresh \ \set{a_i}, \set{b_j}, v_x.\ \
-       	\openrule
-       	{
-       		\gamma_{jpx}^{j\in J_{px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
-       	{t \OTWeakarrow {\alpha_{px}} t_{px}}\qquad (2)
-       	%         \right)
-       	\end{mathpar}
-
-       	such that  $\forall x, \{j\in J_1|\beta_j \neq \tau\}=J_{x}, (s',t_{px}|\Pred\,_{s'\!,{px}})\in 
-       	\mathcal{R}$;
-       	and  \\
-
-       	$\Pred_{s,p} \land \Pred_{OT}\\
-       	\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-       	\left( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_{px}}
-       	\land \alpha\!=\!\alpha_{px} \land
-       	\Pred\,_{s'\!,{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)$\\
-
-For any open transition $OT_{px}$, since
-       	$(t_p,u|\Pred_{p,u})\in\mathcal{R}'$ there exist open transitions
-       	$OT_{pxy}^{y\in Y} \subseteq \mathcal{T}_3$:
-
-       	\begin{mathpar}  	
-       	%    \left( fresh \ \set{a_i}, \set{b_j}, v_x.\ \
-       	\openrule
-       	{
-       		\gamma_{jpxy}^{j\in J_{pxy}}, 
-       		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
-       	{u \OTWeakarrow {\alpha_{pxy}} u_{pxy}}\qquad (3)
-       	%         \right)    	
-       	\end{mathpar}
-       	such that  $\forall y, J_{px}=J_{pxy}, 
-       	(t_{px},u_{pxy}|\Pred_{{px,pxy}})\in \mathcal{R}'$; and  \\
-       	$\Pred_{p,u} \land \Pred_{OT_{px}}\\
-       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
-       	\left( \forall j. \vis{\beta_{jpx}}=\gamma_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
-       	\land \alpha_{px}\!=\!\alpha_{pxy} \land
-       	\Pred_{{px,pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.\\
-
-This is verified for all $p \in P$. Overall,  we have a family of open 
-       	transitions 
-       	$OT_{xy}^{p\in P, x\in X, 
-       		y\in Y} \subseteq \mathcal{T}_3$ that should simulate \emph{OT}.
-
-------------------------------------------------------------------
-
-We have  $\forall y, \forall x, \forall p \in P,  \{j \in J_1|\,\beta_j\neq \tau\} =J_{px}=J_{pxy}, 
-       	({s}',u_{pxy}|\Pred_{s',{pxy}})\in \mathcal{R}''$ for some $\Pred_{{s',pxy}}$.  Indeed,  for any $p$, $x$ and $y$,  we have
-$(s',t_{px}|\Pred_{{s'\!,px}})\in \mathcal{R}$
-       	and $(t_{px},u_{pxy}|\Pred_{{px,pxy}})\in \mathcal{R}'$. For states ensuring the transitivity relation we have   
-       		 for all $p$, $x$, $y$, $\Pred_{px}\land 
-       	\Pred_{{px,pxy}}\implies 
-       	\Pred_{{s'\!,pxy}}$.
-
-\TODO{We need to prove that we have the following  relation:}  \\     	
-       	\begin{small}
- $\Pred_{s,u} \land \Pred_{OT}\\
-       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\!\!\bigvee_{y\in Y}\!\!\bigvee_{p\in P}
-       		\left( \forall j. \vis{\beta_j}=\gamma_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
-       		\land \alpha\!=\!\alpha_{pxy} \land
-       		\Pred_{{s',\!xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
-       	\end{small}
-
-\noindent By rule given in (2) we have for all $p$:\\
-\begin{small}
-$\big(\Pred_{s,p} \land \Pred_{OT}\big)\land\Pred_{p,u}\\
-       		\hspace{1cm} \implies\!\!\! \Big(\bigvee_{x\in X}
-       		\left( \forall j. \vis{\beta_j}=\gamma_{jpx}  \Rightarrow \Pred_{OT_{px}}
-       		\land \alpha\!=\!\alpha_{px} \land
-       		\Pred_{{s'\!,px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\Big)\land\Pred_{p,u}\\
-       		%
-       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\!
-       	\Big( \forall j.\vis{\beta_j}\!=\!\gamma_{jpx}  \Rightarrow 
-       		(\Pred_{OT_{px}}\land\Pred_{p,u})
-       		\land \alpha\!=\!\alpha_{px} \land
-       		\Pred_{{s'\!,px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\Big).\\
-       		%
-       		$
-  \end{small}
-
-\noindent By rule given in (3) we have:   \\
-$\Pred_{p,u} \land \Pred_{OT_{px}}\\
-       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
-       	\left( \forall j. \gamma_{jpx}=\gamma_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
-       	\land \alpha_{px}\!=\!\alpha_{pxy} \land
-       	\Pred_{{px,pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.\\
-
-\noindent So can rewrite the formula as:\\	
-\begin{small}
-$ \big(\Pred_{s,p} \land \Pred_{OT}\big)\land\Pred_{p,u}\\
-\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-       	\bigg( \forall j.\vis{\beta_j}\!=\!\gamma_{jpx}  \Rightarrow\\~~\hspace{2em}
-       		\Big(\!\bigvee_{y\in Y}
-       			\left( \forall j'. \gamma_{j'px}\!=\!\gamma_{j'pxy}  \Rightarrow \Pred_{OT_{pxy}}\!\land \alpha_{px}\!=\!\alpha_{pxy}
-\land \Pred_{{px,pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)   \Big)\\~~ \hspace{2em} \land \alpha\!=\!\alpha_{px} \land
-       		\Pred_{{s'\!,px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\bigg).\\
-\hspace{1cm}\implies\!\!\!\!\bigvee_{x\in X} \bigvee_{y\in Y}\bigg(\forall j, j'.\vis{\beta_j}\!=\!\gamma_{jpx}\!\land\!\gamma_{j'px}\!=\!\gamma_{j'pxy}
- \Rightarrow\\~~\hspace{2em} \Big(\Pred_{OT_{pxy}}\!\land\alpha\!=\alpha_{px}\!=\!\alpha_{pxy} \land 
-       \Pred_{{px,pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}
-       		\land
-\Pred_{{s'\!,px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\Big)\bigg).
-       		$
-       \end{small}
-
-\medskip
-\noindent Because of variables domains independence we  have:\\ 
-    $\Pred_{{s'\!,px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\land 
-       	\Pred_{{px,pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}
-       	\Leftrightarrow\\ % we changed =
-\Pred_{{s'\!,px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land
-       \Pred_{{px,pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}} \Leftrightarrow
-\big(\Pred_{{s'\!,px}} \land   \Pred_{{px,pxy}}\big)   \subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}} \\	\implies\Pred_{{s'\!,pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}
-\subst{\Post_{OT_{pxy}}}\Leftrightarrow  \Pred_{{s'\!,pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}} $\\
-
-\noindent This allows us to conclude with $\Pred_{s,u} = \bigvee_{p\in P} 
-       	\Pred_{s,p}\land\Pred_{p,u}$:
-
-      	\begin{small}     	
-$\Pred_{s,u} \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \bigvee_{p\in P} \big(
-	\Pred_{s,p}\land\Pred_{p,u}\big) \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\!\bigvee_{p\in P}\bigg(\!\!
- \bigvee_{x\in X}\!\!\bigvee_{y\in Y}\!\!
-\Big( \forall j, j'.\vis{\beta_j}\!=\!\gamma_{jpx} \land \gamma_{j'px}\!=\!\gamma_{j'pxy}\Rightarrow\\~~\hspace{2em}
-\Big( 
-\Pred_{OT_{pxy}}
-\land \alpha\!=\alpha_{px}\!=\!\alpha_{pxy} \land
-\Pred_{{s'\!,pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\Big)\Big)\bigg)
-\\
-\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\!\!\bigvee_{y\in Y}\!\!\bigvee_{p\in P}\!\!
-\Big(\forall j.\vis{\beta_j}\!=\!\gamma_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
-\land\, \alpha\!=\!\alpha_{pxy} \land
-\Pred_{{s'\!,pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\Big)$.
-  \end{small}
 

### 2019-09-06 2016-Weak-FH-Bisim/WeakBisim.tex
un peu de biblio

@@
 %% Note that
+
+\section{Related Works}
+
+In
+\cite{Johnson:2013:CBSE,Johnson:2014:qosa}, the authors investigate several methodologies for the compositional verification of software systems, with the aim to verify reconfigurable component systems.
+To improve scaling and compositionality, the authors  decouple the verification problem that is to be resolved by a SMT (satisfiability modulo theory) solver into independent sub-problems on independent sets of variables.
+These works clearly highlight the interest of incremental and compositional verification in a very general setting.
+By adding more structure to the composition model and designing a dedicated bisimulation theory, we show here how to enforce a compositional proof system that is more powerful than independent sets of variables.
+Our theory has also been encoded into an SMT solver and it would be interesting to investigate how the examples of evolving systems studied by the authors could be encoded into pNet and verified by our framework.
+However, the models of Johnson et al.
+are quite different from ours, in particular they are much less structured, and translating them is clearly outside the scope of this article.
+Additionally, the more compositional constraint resolution provided by the authors could also be interesting to make our SMT proofs scale better (inside a single pNet for example), the integration of the Z3 framework described in \cite{Johnson:2014:qosa} with our proof theory for open pNets would also be worth investigating from a practical point of view.
 

### 2019-09-11 2016-Weak-FH-Bisim/WeakBisim.tex
qq commentaires en plus
correct lemma 8 + start thm 3bis

@@
 
+\TODO{rertavailler le paragraphe ci dessous}
 In
@@
 Additionally, the more compositional constraint resolution provided by the authors could also be interesting to make our SMT proofs scale better (inside a single pNet for example), the integration of the Z3 framework described in \cite{Johnson:2014:qosa} with our proof theory for open pNets would also be worth investigating from a practical point of view.
+One major different however is that pNets in their current state are not much adapted to probabilistic verification contrarily to \cite{Johnson:2014:qosa} but they are better suited to verify complex behavioural properties.
 
@@
 $s_i=s_{10 i} \wedge s_{1(m_1+1) i}=s_{20i} \wedge  s_{21i}= s_{30 i} \wedge s_{3(m_2+1) i}=s'_i$\\
-\[\alpha=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}}\]
-\begin{multline*}
-\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \\
-\dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{1p}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\Post_{1j}}}
-\end{multline*}
-\begin{multline*}
-\Pred=\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\big)\land\Pred^2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\ \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}
-\end{multline*}
-\begin{equation*}
-\begin{split}
-\Post&=\bigotimes_{p=m_2}^{0}\Post_{3p}\otimes\Post_2\otimes\bigotimes_{j=m_1}^{0}\Post_{1j}
-\end{split}
-\end{equation*}
+$\alpha=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}}$\\
+%\begin{multline*}
+$\gamma_j^{j\in J}=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup \, \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}}} \\
+~~\qquad~\dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{3p}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\Post_{1j}}}$\\
+%\end{multline*}
+%\begin{multline*}
+$\Pred=\displaystyle{\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\big)\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land}$\\ 
+$~~\qquad\quad\displaystyle{\bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}}$\\
+$\Post=\displaystyle{\bigotimes_{p=m_2}^{0}\Post_{3p}\otimes\Post_2\otimes\bigotimes_{j=m_1}^{0}\Post_{1j}}$
+%\end{multline*}
 
 Note that, for $l\in\{1,3\}$ if $\beta_{l p j_0}=\tau$, then, because of Definition \ref{def:Non-ObsTau}, $P$ necessarily makes a $\tau$ open transition and remains in the same state, ($s_p = s_{p+1}$).
-Thus without loss of generality, we can bypass such an open transition and obtain another decomposition of the WOT without the open transition that requires ${\beta^l_{p{j_0}}}=\tau$.
-We can thus  suppose that for all $p$ and $l$ we have ${\beta_{l p{j_0}}}\neq\tau$ or $j_0\not\in J_{1 p}$.
+Thus without loss of generality, we can bypass such an open transition and obtain another decomposition of the WOT without the open transition that requires ${\beta_{lp{j_0}}}=\tau$.
+We can thus  suppose that for all $p$ and $l$ we have ${\beta_{lp{j_0}}}\neq\tau$ or $j_0\not\in J_{1 p}$.
 To avoid a special case, we suppose that the hole $j_0$ moves during the OT $\alpha'$, i.e.
-$\beta_{2 \j_0}=\beta_{m}$ for some $m$.
+$\beta_{2 j_0}=\beta_{m}$ for some $m$.
 Additionally, $\beta_{m}\neq \tau$, else we would have $\alpha=\alpha'=\tau$ and the $\alpha'$ OT could be also removed from the reduction, leading to a particular and simpler case.
@@
 
+\begin{theorem}[Congruence]\label{thm-congr-weq}
+	Consider an open pNet:
+	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
+	\set{\symb{SV}}\myrangle$.
+	Let $j_0\in J$ be a hole. Let $\pNetQ$ and $\pNetQ'$ be two weak FH-bisimilar pNets such that 
+	$\Sortop(\pNetQ)=\Sortop(\pNetQ')=\Sort_{j_0}$. Then 
+	$\pNet[\pNetQ]_{j_0}$ and 
+	$\pNet[\pNetQ']_{j_0}$ are weak FH-bisimilar.
+\end{theorem}
+ \begin{proof}  (Sketch of proof) Consider $Q$ weak FH-bisimilar to $Q'$.
+It means, according to Lemma  \ref{lem-alternative-weak-bisim} for any weak open transition $WOT$ in $Q$ there exist a family of weak open transitions $WOT_{x}^{x \in X}$ in $Q'$.
+We apply  Lemma \ref{lem-Weakcompose1} on weak open transition $WOT$, $j_0 \in J$, we obtain a new weak open transition $WOT'$ in $P[Q]_{j_0}$.
+On other hand, we apply same Lemma \ref{lem-Weakcompose1} on each weak open transitions $WOT_{x}$, so we obtain a new family of weak open transitions $WOT_{x}'$ in $P[Q']_{j_0}$.
+ \end{proof}
+\begin{theorem}[Context equivalence]\label{thm-ctxt-weq}
+	Consider two FH-bisimilar open pNets:
+	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
+	\set{\symb{SV}}\myrangle$ and 	$\pNet' = \mylangle {\pNet'}_i^{i\in I}, 
+	\Sort_j^{j\in 
+	J}, 	\set{\symb{SV'}}\myrangle$ 
+	(recall they must have the same holes to be bisimilar).
+	Let $j_0\in J$ be a hole, and $Q$ be a pNet such that $\Sortop(Q)=\Sort_{j_0}$. Then 
+	$\pNet[Q]_{j_0}$ and 
+	$\pNet'[Q]_{j_0}$ are FH-bisimilar.
+\end{theorem}
   \newpage

### 2019-09-20 2016-Weak-FH-Bisim/WeakBisim.tex
review lemma 8 + Thm 11

@@
 }\\
-\text{~~and for all $t\in[0..n]$~~}
+\text{~~and for all $p\in[0..n]$~~}
 Q\models{\openrule
 	{
-		\gamma_{t j}^{j\in J_t},
-		 \Pred_t,  
-		\Post_t}
-	{\ostate{s_{t i}^{i\in L_Q}} \OTWeakarrow {\alpha_t}
-		\ostate{s_{(t+1) i}^{\, i\in L_Q}}}
+		\gamma_{pj}^{j\in J_p},
+		 \Pred_p,  
+		\Post_p}
+	{\ostate{s_{pi}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
+		\ostate{s_{(p+1) i}^{\, i\in L_Q}}}
 }%\]
@@
 \begin{mathpar}
-J_Q=\displaystyle{\bigcup_{t=0}^nJ_{t}}
+J_Q=\displaystyle{\bigcup_{p=0}^nJ_{p}}
 \qquad
-\Pred\,'=\Pred\land \bigwedge_{t=0}^{n}(\alpha_t=\beta_t\land \Pred_t)\bigotimes_{i=t-1}^{0}\Post_i
+\Pred\,'=\Pred\land \bigwedge_{p=0}^{n}(\alpha_t=\beta_t\land \Pred_t)\bigotimes_{i=p-1}^{0}\Post_i
 \\
-\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}\subst{\bigotimes_{k=t}^{0}{\Post_k}}}\text{\quad and\quad}
-\Post\,'=\Post\uplus\bigotimes_{t=n}^{0}
-		\Post_t
+\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}\subst{\bigotimes_{k=p}^{0}{\Post_k}}}\text{\quad and\quad}
+\Post\,'=\Post\uplus\bigotimes_{p=n}^{0}
+		\Post_p
 \\
@@
 $s_i=s_{10 i} \wedge s_{1(m_1+1) i}=s_{20i} \wedge  s_{21i}= s_{30 i} \wedge s_{3(m_2+1) i}=s'_i$\\
-$\alpha=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}}$\\
+$\alpha=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}}$ \\
 %\begin{multline*}
-$\gamma_j^{j\in J}=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup \, \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}}} \\
-~~\qquad~\dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{3p}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\Post_{1j}}}$\\
+$\gamma_j^{j\in J}=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \dotcup \, \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}} \\
+~~\qquad~\dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{3p}} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}$\\
 %\end{multline*}
@@
 
-Note that, for $l\in\{1,3\}$ if $\beta_{l p j_0}=\tau$, then, because of Definition \ref{def:Non-ObsTau}, $P$ necessarily makes a $\tau$ open transition and remains in the same state, ($s_p = s_{p+1}$).
+Note that, for $l\in\{1,3\}$ if $\beta_{l p j_0}=\tau$, then, because of Definition \ref{def:Non-ObsTau}, $P$ necessarily makes a $\tau$ open transition and remains in the same state, e.g.
+$s_{1pi} = s_{1(p+1)i}$.
 Thus without loss of generality, we can bypass such an open transition and obtain another decomposition of the WOT without the open transition that requires ${\beta_{lp{j_0}}}=\tau$.
@@
 We introduce $n_i^{i\in[0..m-1]}$, and $(n'_i)^{i\in[m+1..n]}$ the indices of the steps in 
-which the hole $j_0$ moves in the 3 sets of OTs above ($\beta_m$ is the action that matches the hole $j_0$ in the OT $\alpha'$), in other words, we have for all $i$, $\beta_{1 n_i j_0}$ a visible action, as additionally:
-\begin{equation*}
-\begin{split}
-\gamma_{j_0}&=[\beta_0..\beta_n]\\
-&=\mybigdotcup_{\substack{i=0\\j_0\in J_{1i}}}^{m_1} \vis{{\beta_{1ij_0}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{{\beta_{2j_0}}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{\substack{i=0\\j_0\in J_{3i}}}^{m_2} \vis{{\beta_{3ij_0}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\Post_{1j}}}
-\end{split}
-\end{equation*}
-
-We have, by definition of $n_i$ and $n'_i$:
-\begin{equation*}
-\begin{split}
-\forall{i\in[0..m-1]},&\beta_{1 n_i j_0}\subst{\bigotimes_{j=n_i-1}^{0} \Post_{1j} }=\beta_i\\ 
-&
-\beta_{2 j_0}\subst{\bigotimes_{j=m_1}^{0} \Post_{1j} }=\beta_m\\ 
-\forall{i\in[m+1..n]},&\beta_{3 n'_i j_0}\subst{\bigotimes_{j=n'i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\Post_{1j}}=\beta_i\\ 
-\end{split}\end{equation*}
-
-Now, we compose OTs for each of the case above (OTs of $P$)':
+which the hole $j_0$ moves in the 3 sets of OTs above ($\beta_m$ is the action that matches the hole $j_0$ in the OT $\alpha'$), in other words, we have for all $i$, $\beta_{1 n_i j_0}$ a visible action, as additionally:\\
+$\gamma_{j_0}=[\beta_0..\beta_n]\\
+~~\quad =\displaystyle{\mybigdotcup_{\substack{i=0\\j_0\in J_{1i}}}^{m_1} \vis{{\beta_{1ij_0}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \dotcup \vis{{\beta_{2j_0}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}} \\
+~~\quad~\displaystyle{ \dotcup \mybigdotcup_{\substack{i=0\\j_0\in J_{3i}}}^{m_2} \vis{{\beta_{3ij_0}} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}}$\\
+
+\noindent We have, by definition of $n_i$ and $n'_i$:\\
+$\displaystyle{\forall{i\in[0..m-1]}, \beta_{1 n_i j_0}\subst{\bigotimes_{k=n_i-1}^{0}\Post_{1k}}=\beta_i}$, $\displaystyle{\beta_{2 j_0}\subst{\bigotimes_{k=m_1}^{0} \Post_{1k} }=\beta_m}$, and \\
+$\displaystyle{\forall{i\in[m+1..n]}, \beta_{3 n_i' j_0}\subst{\bigotimes_{k=n_i'-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}=\beta_i}$\\
+
+\noindent Now, we compose OTs for each of the case above (OTs of $P$):
 \begin{enumerate}
-\item $p\in [0..m_1]$. Either there is $i$ such that $p=n_i$, and thus $\beta_i$ and $\beta_{1 p j_0}$ are defined. In this case by Lemma~\ref{lem-Weakcompose1}, we have:
-
-Then, we have\\[-2ex]
+\item For the first $\tau$ OTs, i.e, $p\in [0..m_1]$. We have: \\
+Either there is $i$ such that $p=n_i$, and thus $\beta_i$ and $\beta_{1 p j_0}$ are defined. In this case by Lemma~\ref{lem-Weakcompose1},  we have: 
 \[ P[Q]_{j_0}  
@@
 			\set{\gamma'_{1p}}, 
-			\Pred_{1p}\,',  \Post_{1p}\,'
+			\Pred\,'_{1p},  \Post\,'_{1p}
 			 }
@@
 	\]
-with 
-\begin{mathpar}
-\set{\gamma'_{1p}}=\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{1pj}^{j\in J_{1p}\setminus \{j_0\}}}\\
-\Pred\,'_{1p}=\Pred_{1p}\land (\beta_{1pj_0}=\alpha_i\land \Pred_i)
-\\
-%\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
-\Post\,'_{1p}=\Post_{1p}\uplus\Post_i
-\end{mathpar}
+with \\
+
+$ \set{\gamma'_{1p}}=\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{1pj}^{j\in J_{1p}\setminus \{j_0\}}},
+\Pred\,'_{1p}=\Pred_{1p}\land (\beta_{1pj_0}=\alpha_i\land \Pred_i)$, and\\
+
+$ \Post\,'_{1p}=\Post_{1p}\uplus\Post_i$\\
 
@@
 \]
-and thus we also have a weak OT by definition:
+and thus we also have a weak OT by Definition \ref{def:buildweakOT} (rule (\WTDeux)):
 \[P[Q]_{j_0} \models\openrule
@@
 \]
-with 
-\begin{mathpar}
-\set{\gamma'_{1p}}=\set{\vis{\beta_{1p}}}\\
-\Pred\,'_{1p}=\Pred_{1p}\\
-\Post\,'_{1p}=\Post_{1p}
-\end{mathpar}
-
-\item idem for the middle OT with label $\alpha$:
+with \\
+
+$\set{\gamma'_{1p}}=\set{\vis{\beta_{1p}}}, \Pred\,'_{1p}=\Pred_{1p}, \Post\,'_{1p}=\Post_{1p}$\\
+
+\item Similarly, for the middle OT with label $\alpha$:
 \[P[Q]_{j_0}\models\openrule
-         {	\set{\gamma'_2},\Pred_2',\Post_2' }
+         {	\set{\gamma'_2},\Pred\,'_2,\Post\,'_2 }
          {\ostate{{s_{20j}}^{j\in L}\uplus s_{mj}^{j\in L_Q}}\OTWeakarrow {\alpha'} \ostate{{(s_{21j})}^{j\in L}\uplus s_{(m+1)j}^{j\in L_Q}}}\]
-with 
-\begin{mathpar}
-\set{\gamma'_2}=\gamma_{m j}^{j\in J_m}\uplus\vis{\beta_{2j}^{j\in J_2\setminus \{j_0\}}}\\
-\Pred\,'_{2}=\Pred_{2}\land (\beta_{2j_0}=\alpha_m\land \Pred_m)
-\\
-%\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
-\Post\,'_{2}=\Post_{2}\uplus\Post_m
-\end{mathpar}
-
-\item and for the last $\tau$ OTs:
-for $p\in [0..m_2]$. Either there is $i$ such that $p=n'_i$, and thus $\beta_i$ and $\beta_{1 p j_0}$ are defined. In this case by Lemma~\ref{lem-Weakcompose1}, we have:
-
-Then, we have\\[-2ex]
+with\\
+
+$\set{\gamma'_2}=\gamma_{m j}^{j\in J_m}\uplus\vis{\beta_{2j}^{j\in J_2\setminus \{j_0\}}},
+\Pred\,'_{2}=\Pred_{2}\land (\beta_{2j_0}=\alpha_m\land \Pred_m)$, and\\
+
+$\Post\,'_{2}=\Post_{2}\uplus\Post_m$\\
+
+\item For the last $\tau$ OTs, i.e, $p\in [0..m_2]$. We have similarly to the first case:\\
+ Either there is $i$ such that $p=n'_i$, and thus $\beta_i$ and $\beta_{1 p j_0}$ are defined. In this case by Lemma~\ref{lem-Weakcompose1}, we have: 
 	\[ P[Q]_{j_0}  
@@
 	\]
-with 
-\begin{mathpar}
-\set{\gamma'_{3p}}=\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{3pj}^{j\in J_{3p}\setminus \{j_0\}}}\\
+with\\
+
+$\set{\gamma'_{3p}}=\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{3pj}^{j\in J_{3p}\setminus \{j_0\}}}, 
 \Pred\,'_{3p}=\Pred_{3p}\land (\beta_{3pj_0}=\alpha_i\land \Pred_i)
-\\
-%\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
-\Post\,'_{3p} =\Post_{3p}\uplus\Post_i
-\end{mathpar}
+$ and,\\
+
+$\Post\,'_{3p} =\Post_{3p}\uplus\Post_i$\\
 
@@
 \]
-and thus we also have a weak OT by definition:
+and thus we also have a weak OT by definition \ref{def:buildweakOT} (rule (\WTDeux)):
 \[P[Q]_{j_0} \models\openrule
@@
 \]
-with 
-\begin{mathpar}
-\set{\gamma'_{3p}}=\set{\beta_{3p}}\\
-\Pred\,'_{3p} =\Pred_{3p}\\
-\Post\,'_{3p} =\Post_{3p}
-\end{mathpar}
-
+with \\
+
+$\set{\gamma'_{3p}}=\set{\beta_{3p}}, \Pred\,'_{3p} =\Pred_{3p}, \Post\,'_{3p} =\Post_{3p}$
 \end{enumerate}
 
-By definition of weak open transition (Definition~\ref{def:buildweakOT}),
+\noindent By definition of weak open transition (Definition~\ref{def:buildweakOT}, rule \WTTrois),
  we obtain:
@@
 On other hand, we apply same Lemma \ref{lem-Weakcompose1} on each weak open transitions $WOT_{x}$, so we obtain a new family of weak open transitions $WOT_{x}'$ in $P[Q']_{j_0}$.
+
+Suppose we have:\\[-2ex]
+\begin{mathpar}
+%\[
+P\models{\openrule
+	{
+		\beta_j^{j\in J}, 
+		\Pred,  
+		\Post}
+	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
+		\ostate{(s_i')^{\, i\in L}}}
+}
+\quad\text{~~and~~}\quad
+Q\models{\openrule
+	{
+		\set{\gamma},
+		 \Pred_Q,  
+		\Post_Q}
+	{\ostate{s_{i}^{i\in L_Q}} \OTWeakarrow {\alpha_Q}
+		\ostate{(s'_{i})^{\, i\in L_Q}}}
+}%\]
+
+\end{mathpar}
+
+Then, we have by lemma \ref{lem-Weakcompose}: \\[-2ex]
+	\[ P[Q]_{j_0}  
+	\models
+	{\openrule
+		{
+			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
+			\Pred\,',  \Post\,'
+			 }
+		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
+			\ostate{(s_i')^{\, i\in L\uplus L_Q}}}
+	}
+	\]
+
+On the other hand, $Q$ weak FH-bisimilar to $Q'$, so according to  Lemma  \ref{lem-alternative-weak-bisim} there exist a family of weak open transitions $WOT_{x}$:
+ \begin{mathpar}
+    \openrule
+         {
+           \gamma_{j x}^{j\in J_{x}}, \Pred_{Q_x},\Post_{Q_x}}
+         {\ostate{t_{i}^{i\in L_{Q_x}}}\OTWeakarrow {\alpha_x} \ostate{t_{ix}^{i\in L_{Q_x}}}}
+\end{mathpar}
+
+such that...\\
+
+By applying  Lemma \ref{lem-Weakcompose} on each weak open transitions $WOT_{x}$, so we obtain a new family of weak open transitions $WOT_{x}'$ in $P[Q']_{j_0}$:
+
+\[ P[Q']_{j_0}  
+	\models
+	{\openrule
+		{
+			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
+			\Pred\,',  \Post\,'
+			 }
+		{\ostate{s_i^{i\in L} \uplus t_{i}^{i\in L_{Q_x}}} \OTWeakarrow {\alpha}
+			\ostate{(s_i')^{\, i\in L} \uplus t_{ix}^{i\in L_{Q_x}} }}
+	}
+	\]
+
  \end{proof}

### 2019-10-09 2016-Weak-FH-Bisim/WeakBisim.tex
commnets page 10, figure page 16

@@
 \TODO{Rabea: trouver reference !!}
-\TODO{refaire les commentaires}
-To illustrate this work, we use the well-known Alternate bit protocol
-(ABP) \TODO{Ref ?}, that provides safe transport of data between two processes,
-over unsafe media. This protocol has been described and studied using
-many approaches, because it is small enough, and can be easily
-verified using exact finite models. Our version here is more
-ambitious, encoding both the data and the control bits in a symbolic
-way. One can imagine that this could easily be extended using bounded
-integers, as in the sliding window protocol, or with more complex data
-structures, in order to verify realistic protocols.
+To illustrate this work, we use a simple transport protocol, that provides safe transport of data between two processes,
+over unsafe media.
 
@@
 argument, through the two protocol entities $sender$ and
-$receiver$. The underlying network is modelled by two media,
-carrying the message together with a control bit on one way, and an
-acknowledge back from $receiver$ to $sender$. The media can be perfect (safe), or
-faulty (losing or duplicating messages) as shown in
-Fig. \ref{schema:ABP-media}. Remark that the pLTSs shown in
-Fig. \ref{schema:ABP-media} are in fact ``generic'' in the sense that
-they will be instanciated in different ways depending on the number
-and types of the message arguments. This is only a graphical syntax,
+$receiver$.
+The underlying network is modelled by a medium entity transporting messages from the sender to the receiver, and that is able to detect some transport error, and signal it to the sender.
+The return $ack$ message from $receiver$ to $sender$ is supposed to be safe.
+
+This is only a graphical syntax,
 with an obvious semantics for building the corresponding pNets.
 
-Fig. \ref{schema:ABP-composed} \TODO{To be commented}
+Fig.
+\ref{SimpleProt:Spec} shows the Schema of this system, and on the right side, its global specification, expressed as a pNet: it should be equivalent to a simple system where the holes would be connected by a perfect reliable medium.
 
@@
 to the two processes connected simply through a perfect medium.
+
+\TODO{Commenter la figure 2}
 
@@
   \label{OT:ABP}
-At the upper level, the $ABP$ pNet has 2 holes and $Protocol$ has
+At the upper level, the $SimpleSystem$ pNet has 2 holes and $SimpleProtocol$ as
 a subnet. One of its possible open transitions (synchronizing the hole $P$
-with the \emph{Protocol}) is:
+with the $Sender$ within the \emph{SimpleProtocol}) is:
 
@@
  $  OT_1  = \openrule{
-%                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
-%                            \xrightarrow{in(?m,?b)}_{M1}
-      (P\mapsto send(m)); Pred=[m=m']; Post=\{s1\_m:=m\}
-                      }
-  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
-    {\ostate{s_0,m_0,m_0,r_0} \OTarrow{\underline{send(m')}} \ostate{s_1,m_0,m_0,r_0}}
+      (P\mapsto p\_send(m)); Pred=[m=m']; Post=\{s1\_m:=m\}
+                      }
+    {\ostate{s_0,m_0,r_0} \OTarrow{\underline{in(m')}} \ostate{s_1,m_0,r_0}}
     $
@@
 
-  The \emph{Protocol} pNet of Fig. \ref{schema:ABP-composed} has 4 controllers and no holes. One of its possible open-transition (the sender sending $(m,b)$ to the medium) is:
+  The \emph{SimpleProtocol} pNet of Fig. \ref{SimpleProt:Spec} has 3 controllers and no holes. One of its possible open-transition (the sender sending $(m)$ to the medium) is:
 
@@
  $  OT_2  = \openrule{
-%                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
-   %                           \xrightarrow{in(?m,?b)}_{M1}
-   \emptyset; Pred=[send(SV2\_m, SV2\_b)=send(s_1\_m, s_1\_sb);in(SV2\_m, SV2\_b)=in(?m,?b)];  \\ Post=\{m_1\_m:=?m, m_1\_b:=?b, s_2\_sb:=s_1\_sb\}
-                      }
-  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
-    {\ostate{s_1,m_0,m_0,r_0} \OTarrow{\underline{send(SV2\_m, SV2\_b)}} \ostate{s_2,m_1,m_0,r_0}}
+   \emptyset; Pred=[send(SV2\_m)=send(s_1\_m);in(SV2\_m)=in(?m)];  \\ Post=\{m_1\_m:=?m\}
+                      }
+    {\ostate{s_1,m_0,r_0} \OTarrow{\underline{send(SV2\_m)}} \ostate{s_2,m_1,r_0}}
     $
 
-    \ERIC{Apres resolution de l'unification:}
+    That can be simplified to:
+
+    \ERIC{Apres application des substitutions et simplification du predicat:}
 
      $  OT_2  = \openrule{
-%                       1 \xrightarrow{send(m,sb)}_{Sender} 2 ~~
-   %                           \xrightarrow{in(?m,?b)}_{M1}
-      \emptyset; Pred=[s_1\_m=SV2\_m, SV2\_m=?m, s_1\_sb=SV2\_b, SV2\_b=?b];  \\ Post=\{m_1\_m:=?m, m_1\_b:=?b, s_2\_sb:=s_1\_sb\}
-                      }
-  %  {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}
-    {\ostate{s_1,m_0,m_0,r_0} \OTarrow{\underline{send(s_1\_m, s_1\_b)}} \ostate{s_2,m_1,m_0,r_0}}
-    $
-
-    \ERIC{Apres application des substitutions et simplification du predicat:}
-
-     $  OT_2  = \openrule{
-      \emptyset; Pred=\True;  \\ Post=\{m_1\_m:=s_1\_m, m_1\_b:=s_1\_sb, s_2\_sb:=s_1\_sb\}
-                      }
-    {\ostate{s_1,m_0,m_0,r_0} \OTarrow{\underline{send(s_1\_m, s_1\_b)}} \ostate{s_2,m_1,m_0,r_0}}
+      \emptyset; Pred=\True;  \\ Post=\{m_1\_m:=s_1\_m\}
+                      }
+    {\ostate{s_1,m_0,r_0} \OTarrow{\underline{send(s_1\_m)}} \ostate{s_2,m_1,r_0}}
     $
@@
 
-\TODO{Add a reference to the construction (deduction tree) in the forte paper?}
+In \cite{henrio:Forte2016}, we have shown a detailed example of the construction of a complex open transition, building a deduction tree using rules Tr1 and Tr2.
 
@@
 
-\TODO{Eric: full (???) result of the tool execution on the running example on the Simple Prot Spec, and maybe one example on the Impl. OTs presented in latex readable form.}
+\TODO{Eric: full (???) result of the tool execution on the running example on the Simple Prot Spec: Done, on the Counetr version !}
+
+\TODO{:  and maybe one example on the Impl. OTs presented in latex readable form??}
+
+\begin{figure}[t]
+   \centerline{\includegraphics[width=9cm]{ATG/SPSpecOpen}}
+   \caption{Specification OA (version with the error counter)}
+   \label{SimpleProtCounter:SpecOA}
+\end{figure}
 
@@
 \end{definition}
+\TODO{Predicate=True me pose un probleme... typiquement, on a besoin d'une ``condition initiale'', pour avoir des pNets data-oriented equivalents a leur version state-oriebted}
+
 We can now prove that pNet composition  preserves

### 2019-10-09 2016-Weak-FH-Bisim/WeakBisim.tex
work with rabea ; sec 5 ; proofs

--- 2019-09-20 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
-\documentclass{lncs/llncs}
+\documentclass[preprint]{elsarticle}
 
@@
 
-%\newtheorem{theorem}{Theorem}[section]
-\newtheorem{prop}[theorem]{Proposition}
+\newtheorem{theorem}{Theorem}
+\newtheorem{prop}{Proposition}
 %\newtheorem{corollary}[theorem]{Corollary}
-%\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{lemma}{Lemma}
 \newtheorem{algorithm}[theorem]{Algorithm}
 %\newtheorem{remark}[theorem]{Remark}
-%\newtheorem{definition}[theorem]{Definition}
-%\newtheorem{example}[theorem]{Example}
+\newtheorem{definition}{Definition}
+\newtheorem{property}{Property}
+\newtheorem{example}{Example}
 %\newtheorem{problem}[theorem]{Problem}
-%\newtheorem{proof}[theorem]{Proof}
+\newenvironment{proof}{\paragraph{Proof}}{}
 
@@
   between INRIA and ECNU, Shanghai}}
-\author{Ludovic Henrio\inst{1}  \ \ \  Eric Madelaine\inst{1,2} \ \ \ Rab\'ea}
-\institute{Univ. of Nice Sophia Antipolis, CNRS, UMR 7271, 06900 Sophia Antipolis, France
-	\and INRIA Sophia Antipolis M\'edit\'erann\'ee, BP 93, 06902 Sophia Antipolis, France
-}
+\author{Ludovic Henrio  \ \ \  Eric Madelaine \ \ \ Rab\'ea}
+%\institute{Univ. of Nice Sophia Antipolis, CNRS, UMR 7271, 06900 Sophia Antipolis, France
+%	\and INRIA Sophia Antipolis M\'edit\'erann\'ee, BP 93, 06902 Sophia Antipolis, France
+%}
 \date{}                                           % Activate to display a given date or no date
@@
 === en parallele
+
+\tableofcontents
 
@@
 provides the definition of pNets and introduces the notations used in
-this paper. Section~\ref{sec:OT} defines open automata, i.e. automata
+this paper, including the definition of open pNets. 
+Section~\ref{sec:OT} defines open automata, i.e. automata
 with parameters and transitions conditioned by the behaviour of
 ``holes''; a strong bisimulation equivalence for open automata is also
-presented in this section. Section~\ref{section:op-semantics} gives
-the semantics of open pNets expressed as weak automata, and states
+presented in this section. 
+Section~\ref{section:op-semantics} gives
+the semantics of open pNets expressed as open automata, and states
 compositional properties on the strong bisimulation for open
-pNets. Finally, Section~\ref{sec:weak} defines a weak bisimulation
+pNets. 
+Section~\ref{sec:weak} defines a weak bisimulation
 equivalence on open automata and derives weak bisimilarity for pNets,
 together with properties on compositionality of weak bisimulaiton for
-open pNets. Finally, Section~\ref{section:conclusion} concludes the
+open pNets. 
+Finally, Section~\ref{sec:RW} discusses related works and Section~\ref{section:conclusion} concludes the
 paper.
-
-\section{Related works}
-
-\TODO{TODO ... }
 
@@
 Unfortunately, the semantics of pNets and the existing tools at this point were only able to deal with a closed system completely instantiated: pNets could be used as composition operator in the definition of the semantics, which was sufficient to perform finite-state model checking on a closed system, but there was no theory for the use of pNets as operators and no tool for proving properties on open system.
-The semmantics of closed pNets~\cite{AmeurBoulifa2017}, defined as an instantiation of labelled transition systems, is not necessary to understand this article but can be useful to  understand the semantics of pNets in a simpler and more operational setting.
-The theory of pNets as operators able to fully take into account open systems is given in the rest of this article.
+The semantics of closed pNets~\cite{AmeurBoulifa2017}, defined as an instantiation of labelled transition systems, is not necessary to understand this article but can be useful to  understand the semantics of pNets in a simpler and more operational setting.
+The theory of pNets as operators able to fully take into account open systems is given in the following sections.
 
@@
 
-\section{Open Automata: A model of process composition}
+\section{A model of process composition}
 \label{sec:OT}
@@
 action of some holes, the transition occurs if some predicates hold, and can involve a 
-set of state modifications.
-This section defines open automata and a bisimulation theory for them.
+set of state modifications. This section defines open automata and a bisimulation theory for them.
+
+\subsection{Open Automata}
  Open automata are not composition structures but they are made of transitions that are dependent of the actions of the holes, and they can reason on variables (potentially with only symbolic values).
@@
 
-\subsection{Bisimulation for open pNets and Composability}
+\subsection{pNet Composition Properties: composition of open transitions}
+The semantics of open pNets allows us to prove two crucial properties relating pNet composition with pNet semantics: open transition of a composed pNet can be decomposed into open transitions of its composing sub-pNets, and conversely, from the open transitions of sub-pNets,  an open transition of the composed pNet can be built.
+
+We start with decomposition: from one open transition of $P[Q]_{j_0}$, we exhibit 
+corresponding behaviours of $P$ and $Q$, and determine the relation between their 
+predicates:
+\begin{lemma}[Open transition decomposition]\label{lem-decompose} Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$}.
+	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose:
+	\[ P[Q]_{j_0}  
+		\models
+		{\openrule
+			{
+				\beta_j^{j\in J}, \Pred,  
+				\Post}
+			{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
+				\ostate{s_i'^{\, i\in L}}}
+		}
+	\]
+		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.
+		 Then there exist $\alpha_Q$, $\Pred\,'$, $\Pred\,''$, 
+		$\Post\,'$, $\Post\,''$ s.t.:\\[-2ex]
+		%\[
+		\begin{mathpar}
+		P\models{\openrule
+			{
+				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
+				\Pred\,',  
+				\Post\,'}
+			{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {\alpha}
+				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
+		}%\]
+	\vspace{-2.2ex}\\\text{and~~}
+		%\[
+		Q\models{\openrule
+			{
+				\beta_j^{j\in J\cap\Holes(Q)}, \Pred\,'',  
+				\Post\,''}
+			{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
+				\ostate{s_i'^{\,i\in L_Q}}}
+		}%\]
+		\end{mathpar}
+		and  $\Pred \iff \Pred\,'
+		\land \Pred\,''\land \alpha_Q=\beta_{j_0}$, $\Post=\Post\,'\uplus 
+		\Post\,''$ where $\Post\,''$ is the restriction of $\Post$ over variables of 
+		$\Leaves(Q)$.
+\end{lemma}
+
+Lemma \ref{lem-compose} is combining an open transition of $P$ with
+an open transition of $Q$, and building a corresponding transition of
+$P[Q]_{j_0}$, assembling their predicates.
+\paragraph{Lemma~\ref{lem-compose}} {\bf Open transition composition}\\
+	Suppose $j_0\in J$ and:\\[-2ex]
+\begin{mathpar}
+%\[
+P\models{\openrule
+	{
+		\beta_j^{j\in J}, 
+		\Pred,  
+		\Post}
+	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
+		\ostate{s_i'^{\, i\in L}}}
+}%\]
+\text{~~and~~}
+%\[
+Q\models{\openrule
+	{
+		\beta_j^{j\in J_Q},
+		 \Pred\,',  
+		\Post\,'}
+	{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
+		\ostate{s_i'^{\, i\in L_Q}}}
+}%\]
+\end{mathpar}
+Then, we have\\[-2ex]
+	\[ P[Q]_{j_0}  
+	\models
+	{\openrule
+		{
+			\beta_j^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
+			\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0},  
+			\Post\uplus \Post\,'}
+		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {\alpha}
+			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
+	}
+	\]
+
+Note that this does not mean that any two pNets can be composed and produce an open 
+transition. Indeed, the predicate $\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0}$ is often not  satisfiable, for example if the action  $\alpha_Q$ cannot be matched with $\beta_{j_0}$.
+Note also that $\beta_{j_0}$ is  only used as an intermediate term inside formulas in the composed open transition: it 
+does not appear neither as global action nor as an action of a hole.
+
+\subsection{Bisimulation for open pNets -- a Composable Bisimulation Theory}
 \label{section:bisimulation-PN}
@@
 synchronisation with their context.
-As the notions of invisible action varies in different contexts,
-e.g. $tau$ in CCS, and $i$ in Lotos, we will rely here on some set of
-\emph{internal actions} depending on a specific action
-algebra. Naturally, an internal action cannot be synchronised with
+The notions of non-observable action varies in different contexts,
+e.g. $tau$ in CCS, and $i$ in Lotos, we could define classically a set of
+\emph{internal/non-observable actions} depending on a specific action
+algebra. In this paper, to simplify the notations, we will simply use $\tau$ as the single non-observable action; the generalisation of our results to a set of non-observable actions is trivial. 
+Naturally, a non-observable action cannot be synchronised with
 actions of other systems in its environment. 
-We show here that under such assumption of non-observability of internal actions, we can define a weak bisimulation relation that is compositional, in the sense of open pNet composition.
-In this section we will first define a notion of weak transition similar to open transition.
-In fact a weak open transition is made of several open transitions labelled as internal transitions, plus potentially one non-internal open transition.
+We show here that under such assumption of non-observability of $\tau$ actions, see Definition~\ref{def:Non-ObsTau}, we can define a weak bisimulation relation that is compositional, in the sense of open pNet composition.
+In this section we will first define a notion of weak open transition similar to open transition.
+In fact a weak open transition is made of several open transitions labelled as non-observable transitions, plus potentially one observable open transition.
 This allows us to define weak open automata, and a weak bisimulation relation based on these weak open automata.
@@
 
-Intuition: tau is non observable if the automaton allows any tau transition from holes, and the global transition resulting from a tau in a hole is a tau transition not changing the action state.
+We first specify in terms of open transition, what it means for an action to be non-observable.
+Namely, we constraint ourselves to system where the emission of a $\tau$ action by a sub-pNet cannot be observed by the surrounding pNets.
+In other words, a pNet cannot change its state, or emit a specific observable action when one of its holes emits a $\tau$ action.
+
+More precisely, we state that $\tau$ is not observable if the automaton always allows any $\tau$ transition from holes, and additionally the global transition resulting from a $\tau$ action of a hole is a $\tau$ transition not changing the pNet's state.
 We define $\Id(s)$ as the identity function on variables of state s.
-\begin{definition}[Non-observability of silent actions]\label{def:Non-ObsTau}
-An open automaton $A = <J,\mathcal{S},s_0,\mathcal{T}>$ \emph{cannot observe silent actions} if and only if for all $j$ in $J$ and $s$ in $\mathcal{S}$ we have
+\begin{definition}[Non-observability of $\tau$ actions]\label{def:Non-ObsTau}
+An open automaton $A = <J,\mathcal{S},s_0,\mathcal{T}>$ \emph{cannot observe $\tau$ actions} if and only if for all $j$ in $J$ and $s$ in $\mathcal{S}$ we have:
 \begin{enumerate}
@@
 and 
-\item for all $A$, $\alpha$,  $s$, $\Post$ and $s'$ such that
+\item for all $\beta_j$, $J$,  $\alpha$,  $s$, $s'$, $\Pred$, $\Post$  such that
 \[ \openrule
@@
          {s \OTarrow {\alpha} s'}
-         \in \mathcal{T} \] If there is a $j$ such that $\beta_j=\tau$ then we have \[ \alpha=\tau\land s=s'\land \Pred=\True\land\Post=\Id(s) \land J=\{j\})
+         \in \mathcal{T} \] If there exists $j$ such that $\beta_j=\tau$ then we have: \[ \alpha=\tau\land s=s'\land \Pred=\True\land\Post=\Id(s) \land J=\{j\}
 \]
@@
 \end{definition}
-The first statement of the definition state that the open automaton must allow a hole to do a silent action at any time, and must not observe it, i.e.
+The first statement of the definition states that the open automaton must allow a hole to do a silent action at any time, and must not observe it, i.e.
 cannot change its internal state because a hole did a $\tau$ transition.
-The second statement ensures that there cannot be in the open automaton other transitions that would be able to observe a silent action from a hole.
-The condition $J=\{j\}$ is a bit restrictive, it could safely be replaced by $\forall j\in J.\, \beta_j=\tau$, allowing the other holes to perform silent transitions too (because these silent actions cannot be observed).
-
-We then can add any number of $\tau$ transitions of the holes before or after any open transition freely.
+The second statement ensures that there cannot be in the open automaton other transitions that would be able to observe a $\tau$ action from a hole.
+The condition $J=\{j\}$ is a bit restrictive, it could safely be replaced by $\forall j\in J.\, \beta_j=\tau$, allowing the other holes to perform $\tau$ transitions too (because these $\tau$ actions cannot be observed).
+
+Consequently, it is possible to add any number of $\tau$ transitions of the holes before or after any open transition freely.
 This property justifies the fact that we can abstract away $\tau$ transitions from holes in the definition of a weak open transition.
 
+\TODO{stopped here}
+
 Classically, we start by defining a derived transition relation based
-on sequences of invisible actions:
+on sequences of invisible actions.
 
@@
 \TODO{Eric: try to draw (ATG) the weak transitino versions of the Simple Protocol, both Spec (easy) and Impl (check readability?)}
+
+\subsection{Composition properties: composition of weak open transitions}
+Now the semantics of an open pNet is defined both as an open automaton, and as a weak open automaton.
+Like the open automaton, the weak open automaton features valuable composition properties.
+We can exhibit  a composition property and a decomposition property that relate open pNet composition with their semantics, defined as weak open automata.
+These are technically more complex than the ones for open automata because each hole performs a set of actions, and thus a composed transition is the composition of one transition of the top-level pNet and a sequence of transitions of the sub-pnet that fills its hole.
 
@@
 
+\subsection{Properties of weak bisimulation for open pNets}
+
 \begin{theorem}[Congruence for  weak bisimulation]\label{weak-thm-congr-eq}
@@
 pick all $\tau^*$ and $\tau^*;a;\tau^*$ sequences from the OA, and build a weak
-OT from each sequence. Here is one example of a short sequence,
+open trnsition from each sequence. Here is one example of a short sequence,
 starting with the open transition $OT_2$ of page \pageref{OT:ABP},
@@
 receiver control bits are equal), and to the environment. The two
-firts OTs are internal, the last one is visible, so it constitute a
+firsts open transitionTs are internal, the last one is visible, so it constitute a
 $\tau;\tau;a$ weak transition.
@@
 
-\section{Related Works}
+\section{Related Works}\label{sec:RW}
 
@@
        		P, x\in X, 
-       		y\in Y} \subseteq \mathcal{T}_3$ that should simulate \emph{OT}.
+       		y\in Y} \subseteq \mathcal{T}_3$ that should simulate $OT$.
 
@@
 between the context and the internal pNet, and with their recomposition.
-We start with decomposition: from one open transition of $P[Q]_{j_0}$, we exhibit 
-corresponding behaviours of $P$ and $Q$, and determine the relation between their 
-predicates:
-
-\begin{lemma}[OT decomposition]\label{lem-decompose} Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$}.
+
+\paragraph{Lemma~\ref{lem-decompose}}: {\bf Open transition decomposition} \\
+ Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$}.
 	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose:
@@
 		$\Leaves(Q)$.
-\end{lemma}
 
@@
 
-Now focus on OTs of the subnets. For each $m\in I_1\uplus I_2$ we have one of the two 
+Now focus on OTs\footnote{In the appendix we use OT to abbreviate ``open transition'' and WOT to stand for ``weak open transition.''} of the subnets.
+For each $m\in I_1\uplus I_2$ we have one of the two
 following OT\footnotemark[\thefootnote]:\\
@@
 
-Lemma \ref{lem-compose} is combining an open transition of $P$ with
-an open transition of $Q$, and building a corresponding transition of
-$P[Q]_{j_0}$, assembling their predicates.
-
 \begin{lemma}[Open transition composition]\label{lem-compose} 
@@
 \end{lemma}
-\TODO{important comment added:}
+
 Note that this does not mean that any two pNets can be composed and produce an open 
@@
 
-\TODO{attention a l ordre: inverse d avant mais colle mieux a la notation -- check everywhere below}
 \subsection{Weak bisimulation is an equivalence}
+
+In this section, we first define two alternative definitions for weak bisimulation.
+We use these two alternative definitions to show that weak bisimulation is an equivalence, we will also re-use these alternative definitions in the  proofs of the theorems in next sections.
 
@@
 
- and similarly for $\Pred_{4i}$, $\Pred_{5i}$, $\Post_{4i}$, and $\Post_{5i}$  \TODO{define or OK this way?}
-
-We have the following assertions:\\
+ and similarly for $\Pred_{4i}$, $\Pred_{5i}$, $\Post_{4i}$, and $\Post_{5i}$.
+
+Also, we have the following assertions:\\
 $
@@
            \gamma_{j a}^{j\in J_{a}}, \Pred_{OT_a},\Post_{OT_a}}
-         {u \OTWeakarrow {\alpha_{1 a}} u_a}
+         {t \OTWeakarrow {\alpha_{1 a}} u_a}
 \end{mathpar}
- such that  $\forall a, J_{a}=\{j\in J_1'|\beta_{1j}\neq\tau\}, u=t,  (s_{11},u_a|\Pred_{s_{11},u_a})\in \mathcal{R}$ and \\
+ such that  $\forall a, J_{a}=\{j\in J_1'|\beta_{1j}\neq\tau\},   (s_{11},u_a|\Pred_{s_{11},u_a})\in \mathcal{R}$ and \\
  $\Pred_{s,t} \land \Pred_1\\
@@
            \gamma_{j a}^{j\in J_{a}}, \Pred_{OT_a},\Post_{OT_a}}
-         {u \OTWeakarrow {\tau} u_a}
+         {t \OTWeakarrow {\tau} u_a}
 \end{mathpar}
@@
 		\Pred, \Post}  
-         {u \OTWeakarrow {\alpha''} w_{c}} 
+         {t \OTWeakarrow {\alpha''} w_{c}} 
 } 
@@
      \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,})$\\
-     Let's start with the hypothesis \TODO{ je vois pas ce que u=t apporte -- Ludo} and consider  $u=t$   we have:\\
+We have:\\
 $\Pred_{OT}= \Pred_1 \wedge \Pred_2\subst{\Post_1} \wedge \Pred_3\subst{\Post_2\shortotimes\Post_1}$\\
@@
 
+\TODO{attention theorem 10 est le thm 6 en fait -- presentation des thm et preuve a revoir}
 \begin{theorem}[Weak FH-Bisimulation is an equivalence]\label{thm-weak-equiv} Suppose $\mathcal{R}$ 
@@
 \subsection{Composition properties}
-
-\begin{lemma}[Weak OT decomposition]\label{lem-decomposeWOT} 
+This section gives detailed lemmas and their proofs, these are the equivalent of the composition lemmas for open transitions, but applied to weak automata that give the semantics of open pNets.
+
+\begin{lemma}[Weak open transition decomposition]\label{lem-decomposeWOT} 
 	Let $\Leaves(Q)=pLTS_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
@@
 				}%\]
-,$
+,$  \\
 $ Q\models{\openrule
@@
 $
-and
+and \\
 $\forall p \in [0..n_2] Q\models{\openrule
@@
 \end{equation*}
-We can optain similar equations for $\alpha_{n_1+1}$ related with $\beta_{2 j_0}$ and the  $\alpha_k$ for $k\geq n_1+2$ related with $\beta_{3 p j_0}$ for some $p$.
+We can obtain similar equations for $\alpha_{n_1+1}$ related with $\beta_{2 j_0}$ and the  $\alpha_k$ for $k\geq n_1+2$ related with $\beta_{3 p j_0}$ for some $p$.
 Note that the substitutions are however more complex.
-\TODO{detailler les equations?}
-
-Overall we obtain (we skip here the details about the three cases 1, 2, and 3 above that all fall into the same equation because of the re-indexing we perform) \[\Pred_\beta \iff \gamma_{j_0}=
-\vis{[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post''_{j}}|p\in[0..n_1+n_2+2]]}\]
+Overall we obtain (we skip here the details about the three cases 1, 2, and 3 above that all fall into the same equation because of the re-indexing we perform): 
+\begin{equation}\label{eqproofbeta}
+\Pred_\beta \iff \gamma_{j_0}=
+\vis{[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post''_{j}}|p\in[0..n_1+n_2+2]]}
+\end{equation}
 
@@
 
-Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (are $\tau$ transition).
-By considering $\tau$  actions we split the sequence of actions into $n+1$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.
-We can decompose each of the $n+1$ subsequences;
-
+Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (they are $\tau$ transitions).
+By considering the sequence of $\tau$ and non-$\tau$ actions we split the sequence of actions into $n+1$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.
+
+\begin{figure}
+\begin{center}
 \includegraphics[width=6cm]{XFIG/proof-explain}
-
-for $k\in [0..n]$ the position of the $k^{\text{th}}$ visible action is  $n_k$, for $k\in [1..n]$,  $n'_k$ is any index between $n_{k-1}$ and $n_k$, additionally $n'_0=0$ and $n'_{n+1}=n_1+n_2+3$.
+\end{center}\caption{Composition of the subsequences}\label{figproof}
+\end{figure}
+
+ We can decompose each of the $n+1$ subsequences in the following way (see Figure~\ref{figproof}).
+For $k\in [0..n]$ the position of the $k^{\text{th}}$ visible action is  $n_k$.
+For $l\in [1..n]$,  $n'_l$ is any index between $n_{l-1}$ and $n_l$, additionally $n'_0=0$ and $n'_{n+1}=n_1+n_2+3$.
 We obtain $n+1$ subsequences  made of the following OTs, for all $k\in [0..n]$ :\\
@@
 				}%\]
-,$ 
+,$ \\
 $Q\models{\openrule
@@
 $
-and
+and\\
 $\forall p \in [(n_k\!+\!1)..(n'_{k+1}\!-\!1)]\,\, Q\models{\openrule
@@
 \alpha_k'\displaystyle{\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}}\]
-We now have (the $\alpha'_p$ correspond to the observable $\alpha_k$ actions): \TODO{add ref to eq 1 page above?}
+With~\ref{eqproofbeta}, we now have (the actions $\alpha'_p$ correspond to the observable actions, $\alpha_k$): 
 \begin{eqnarray*}
@@
 
-Indeed, \TODO{fill the empty lines (more complex but easy adaptation)}
+Indeed,
 {\scriptsize \begin{equation*}
@@
 \end{multline*}
-Now, when $j\in J_t$ for some $t$,  $\gamma'_j$ is the concatenation of elements of $\gamma'_{1ij}$, $\gamma_2'$, $\gamma'_{3ij}$  that are not empty.
+Now, when $j\in J_t$ for some $t$,  $\gamma'_j$ is the concatenation of elements of $\gamma'_{1ij}$, $\gamma'_{2 j}$, $\gamma'_{3ij}$  that are not empty.
 By construction the concatenation of these elements is $\gamma_{tj}$, for $t\in[0..n]$.
@@
 \gamma'_j&=
-\mybigdotcup_{i=0}^{m_1}\set{\gamma'_{1i}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{1k}}\dotcup
- \set{\gamma'_{2}}\subst{\bigotimes_{k=m_1}^{0}\Post\,'_{1k}}\dotcup
- \mybigdotcup_{i=0}^{m_2}\set{\gamma'_{3i}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}\\
+\mybigdotcup_{i=0}^{m_1}{\gamma'_{1ij}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{1k}}\dotcup
+ {\gamma'_{2 j}}\subst{\bigotimes_{k=m_1}^{0}\Post\,'_{1k}}\dotcup
+ \mybigdotcup_{i=0}^{m_2}{\gamma'_{3ij}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}\\
 &=
@@
 ~\quad\bigwedge_{i=0}^{m_3}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\Big)\\
-&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\land\Pred^2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\&\qquad \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\Big)\\&\qquad
+&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\&\qquad \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\Big)\\&\qquad
 \land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i\\&\qquad
@@
 ~\quad\bigwedge_{i=m+1}^{n}(\beta_{3{n'_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j=n'_i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\Big)\\
-&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\big)\land\Pred^2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\&\qquad \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\Big)\\&\qquad
+&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\big)\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\&\qquad \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\Big)\\&\qquad
 \land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i\\&\qquad
@@
 
-\TODO{prove the 3 theorems for composability of weak bisim or explain why the proof is similar to strong (thanks to the previous lemmas)}
 \newpage

### 2019-10-09 2016-Weak-FH-Bisim/WeakBisim.tex

@@
 
-\section{A model of process composition}
-\label{sec:OT}
+\section{A model of process composition}\label{sec:OT}
+\TODO{Commenter la figure 2}
 

### 2019-10-10 2016-Weak-FH-Bisim/WeakBisim.tex
Sec 5

@@
 
+Note that for any term $t$ we have: $t\subst{\Post\shortotimes\Post'} = t\subst{\Post}\subst{\Post'}$
+
 \subsection{Parameterised Networks (pNets)}
@@
  FH-bisimulation is defined formally: 
- \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim}
+ \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim} ~\\
 
@@
 
-\subsection{Defining weak open transitions}
+\subsection{Preliminary definitions and notations}
 
@@
 
-Consequently, it is possible to add any number of $\tau$ transitions of the holes before or after any open transition freely.
+By definition, one weak open transition contains  several open transitions, where  each open transition can require an observable action from a given hole, the same hole might have to emit several observable actions for a single weak open transition to occur.
+Consequently, for a weak open transition to trigger, a list of actions from a given hole might be required.
+
+Thus, we let $\gamma$ range over lists of action terms and use $\dotcup$ as the union operator that appends lists of action terms: given two  lists of action terms  $\gamma\dotcup\gamma '$ concatenates the two lists.
+The operation is lifted to indexed sets of lists:  $\set {\gamma_1}\dotcup \set {\gamma_2}$ is an indexed set of lists such that, at each index $i$, $\set {\gamma_1}\dotcup \set {\gamma_2}$ concatenates the list of  actions at index $i$ of $\set{\gamma_1}$ and the one at index $i$ of $\set {\gamma_2}$\footnote{One of the two lists is empty when $i\not \in \dom(\set{\gamma_1})$ or $i\not \in \dom(\set{\gamma_2})$ .}.
+$[a]$ denotes a list with a single element.
+
+As required actions are now sequences of observable actions, we need an operator to build them from set of actions that occur in open transitions.
+Thus we define $\vis{\set\beta}$ as the mapping $\set\beta$  with only observable actions but where each element is either empty or a list of length 1:
+ \[\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}\text{ where }I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}\]
+
+\subsection{Weak open transition definition}
+
+Because of the non-observability property (Definition~\ref{def:Non-ObsTau}), it is possible to add any number of $\tau$ transitions of the holes before or after any open transition freely.
 This property justifies the fact that we can abstract away $\tau$ transitions from holes in the definition of a weak open transition.
 
-\TODO{stopped here}
-
-Classically, we start by defining a derived transition relation based
-on sequences of invisible actions.
+%
+%Classically, we start by defining a derived transition relation based
+%on sequences of invisible actions.
 
 \def\InvAct{\mathcal{Inv}}
-
-\RAB{We let $\gamma$ range over words (of action terms) and use $\dotcup$ as the union that appends words.}
-
-We let $\gamma$ range over lists of action terms and use $\dotcup$ as the union that appends lists of action terms: given two  lists of action terms  $\gamma\dotcup\gamma '$ concatenates teh two lists.
-The operation is lifted to indexed sets of lists where  $\set {\gamma_1}\dotcup \set {\gamma_2}$ is an indexed set of lists that at each index concatenates the listof  list of $\set{\gamma_1}$ and the one of $\set {\gamma_2}$ (where one of the two lists is empty when $j\not \in \dom(\set{\gamma_1})$).
-$[a]$ is a list with a single element.
+%
+%\RAB{We let $\gamma$ range over words (of action terms) and use $\dotcup$ as the union that appends words.}
 
@@
 
-We can rewrite a weak open transition  $ \OTWeakarrow {\alpha}$ as a sequence of open transitions $(\OTarrow{\tau})^* (\OTarrow{\alpha})(\OTarrow{\tau})^* $.
-
-We define $\vis{\set\beta}$ as the mapping $\set\beta$  without  invisible actions but where each element is now a list (if length 1).\\ $\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}$ s.t.
-$I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}$.
-
+A weak open transition labelled $\alpha$ can be seen as a sequence of open transitions that are all labelled $\tau$ except one that is labelled $\alpha$; however conditions on predicates, effects, and states must be verified for this sequence to be enactable.
+
+We are now able to build a weak open automaton from an open automaton.
+This is done in a way that resembles the process of $\tau$ saturation: we add  $\tau$ open transitions before or after another (observable or not) open transition.
 \begin{definition}[Building a weak open automaton]\label{def:buildweakOT}
@@
 The weak open automaton \emph{derived} from $A$ is an open automaton  $<J,\mathcal{S},s_0,\WT>$ where $\WT$ is derived from $\mathcal{T}$ as follows: 
-
 %\noindent{\bf Invisible $\tau$ transitions:}
@@
 \end{definition}
+Rule $\WTUn$ states that it is always possible to do a null $\tau$ transition, where the state is unchanged and the holes perform no action.
+Rule~$\WTDeux$ states that each open transition can be considered as a weak open transition.
+The last rule is the most interesting:  Rule~$\WTTrois$ allows any number of $\tau$ transitions before or after a weak open transition.
+This rules carefully composes predicates, effects, and actions of the holes, indeed in the rule, predicate $\Pred_2$ manipulates variables of $s_1$ that result from the first weak open transition.
+Their value thus depend of the initial state but also of the effect (as a substitution $\Post_1$) of the first weak open transition.
+In the same manner, $\Pred_3$ must be applied the joint substitution $\Post_2\bigotimes\Post_1$.
+Similarly, effects on variables must be applied to obtain the global effect of the composed weak open transition, it must also be applied to observable actions of the holes, and to the global action of the weak open transition.
 
@@
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
-   \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \Rightarrow\! \Pred_{OT_x}
+   \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
      \!\land\! \alpha\!=\!\alpha_x\! \land\!  
@@
        	\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}
-       	\left( \forall j. \beta_j=\beta_{jpx}  \Rightarrow \Pred_{OT_{px}}
+       	\left( \forall j. \beta_j=\beta_{jpx}  \land \Pred_{OT_{px}}
        	\land \alpha\!=\!\alpha_{px} \land
@@
        	\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}\!
-       	\left( \forall j.\beta_{jpx}\!=\!\beta_{jpxy} \Rightarrow\! \Pred_{OT_{pxy}}\!
+       	\left( \forall j.\beta_{jpx}\!=\!\beta_{jpxy} \land\! \Pred_{OT_{pxy}}\!
        	\land\! \alpha_{px}\!=\!\alpha_{pxy} \!\land\!
@@
        		\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
-       		\left( \forall j. \beta_j=\beta_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
+       		\left( \forall j. \beta_j=\beta_{jpxy}  \land \Pred_{OT_{pxy}}
        		\land \alpha\!=\!\alpha_{pxy} \land
@@
        		\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}
-       		\left( \forall j. \beta_j=\beta_{jpx}  \Rightarrow \Pred_{OT_{px}}
+       		\left( \forall j. \beta_j=\beta_{jpx}  \land \Pred_{OT_{px}}
        		\land \alpha\!=\!\alpha_{px} \land
@@
        		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-       		\left( \forall j. \beta_j=\beta_{jpx}  \Rightarrow 
+       		\left( \forall j. \beta_j=\beta_{jpx}  \land 
        		(\Pred_{OT_{px}}\land\Pred_{p,u})
@@
        		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-       		\big( \forall j. \beta_j=\beta_{jpx}  \Rightarrow (\bigvee_{y\in Y} 
-       		\big( \forall j'. \beta_{j'px}=\beta_{j'pxy}  \Rightarrow \Pred_{OT_{pxy}}
+       		\big( \forall j. \beta_j=\beta_{jpx}  \land (\bigvee_{y\in Y} 
+       		\big( \forall j'. \beta_{j'px}=\beta_{j'pxy}  \land \Pred_{OT_{pxy}}
        		\land \alpha_{px}\!=\!\alpha_{pxy}\\~\hspace{3em}~ \land
@@
        		\big( \forall j, j'. \beta_j=\beta_{jpx} \land \beta_{j'px}=\beta_{j'pxy}
-       		\Rightarrow \big( 
+       		\land \big( 
        		\Pred_{OT_{pxy}}
@@
 \big( \forall j, j'.\beta_j=\beta_{jpx} \land \beta_{j'px}=\beta_{j'pxy}
-\Rightarrow\\ ~\hspace{7em} 
+\land\\ ~\hspace{7em} 
 \Pred_{OT_{pxy}}
@@
 \hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
-\left( \forall j. \beta_j\!=\!\beta_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
+\left( \forall j. \beta_j\!=\!\beta_{jpxy}  \land \Pred_{OT_{pxy}}
 \land \alpha\!=\!\alpha_{pxy} \land
@@
  \Rightarrow \displaystyle{\bigvee_{x\in X}
- \left( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \Rightarrow 
+ \left( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \land 
  \Pred_{OT_x}
@@
  	{\displaystyle\bigvee_{x\in X}
- 	\left( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \Rightarrow 
+ 	\left( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \land 
  	\Pred_{OT_x}
@@
  	{\displaystyle\bigvee_{x\in X}
- 		\left( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \Rightarrow 
+ 		\left( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \land 
  		\Pred\,'\land \Pred_{OT_x}
@@
 \[{\displaystyle\bigvee_{x\in X}
- 		\left( \forall j\in J. \beta_j=\beta_{jx}  \Rightarrow 
+ 		\left( \forall j\in J. \beta_j=\beta_{jx}  \land 
  		\left(\Pred\,'\land \Pred_{OT_x}
@@
 		 \Rightarrow \bigvee_{x\in X}
-			\left( \forall j\in J'. \beta_j=\beta_{jx}  \Rightarrow 
+			\left( \forall j\in J'. \beta_j=\beta_{jx}  \land 
 			\Pred_{OT_x}
@@
 {\displaystyle{\bigvee_{x\in X}\!(\forall j\!\in\! J'. \beta_j\!=\!\beta_{jx}  
-\Rightarrow \!
+\land \!
 \Pred_{OT_x}\land \alpha_Q=\beta_{j_0}
@@
 	{\displaystyle{\bigvee_{x\in X}\!(\forall j\!\in\! J'. \beta_j\!=\!\beta_{jx}  
-\Rightarrow \!
+\land \!
 \left(\Pred_{OT_x}\land
@@
 
-We use ${\displaystyle \bigotimes_{i=n}^{0} \Post_i}$ to denote  $\Post_n\otimes ..
-\otimes \Post_0$.
-By convention ${\displaystyle \bigotimes_{i=-1}^{0} \Post_i}$ is the identity.
-Note that for any term $t$ we have: $t\subst{\Post\shortotimes\Post'} = t\subst{\Post}\subst{\Post'}$
+We  define a quantified composition operator for effects, i.e.$\Post$ elements of the open transitions.
+We use ${\displaystyle \bigotimes_{i=n}^{0} \Post_i}$ to denote  $\Post_n\otimes .. \otimes \Post_0$. By convention ${\displaystyle \bigotimes_{i=-1}^{0} \Post_i}$ is the identity.
 
@@
 \displaystyle{\implies\!\!\! \bigvee_{x\in X}
-   \left( \forall j\in J_x.\gamma_j=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
+   \left( \forall j\in J_x.\gamma_j=\gamma_{jx}  \land \Pred_{OT_x}
      \land \alpha\!=\!\alpha_x \land  
@@
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
-  \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a}
+  \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}=\gamma_{ja}  \land \Pred_{OT_a}
      \land \alpha_{1 a}\!=\!\tau \land  
@@
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{b\in B}}
- \!\!  \left( \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}\Rightarrow \Pred_{OT_{b}}\!\land \alpha'\!=\!\alpha_{2 b} \land  
+ \!\!  \left( \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}\land \Pred_{OT_{b}}\!\land \alpha'\!=\!\alpha_{2 b} \land  
      \Pred_{s_{21},v_{b}}\subst{\Post_2\uplus\Post_{OT_{b}}}\right)$
@@
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{c\in C}}
-   \!\left( \forall j\in J_{c}. \vis{\beta_{3j}}\!=\!\gamma_{jc} \! \Rightarrow\! \Pred_{OT_{c}}\!
+   \!\left( \forall j\in J_{c}. \vis{\beta_{3j}}\!=\!\gamma_{jc} \! \land\! \Pred_{OT_{c}}\!
      \land\!  
@@
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} 
-  ( \forall j\in J. \gamma_j'=\gamma_{j}  \Rightarrow \Pred
+  ( \forall j\in J. \gamma_j'=\gamma_{j}  \land \Pred
      \land \alpha \!=\! \alpha'' \land  
@@
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
- \! \! \left( \forall j\in J_a. \vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a}
+ \! \! \left( \forall j\in J_a. \vis{\beta_{1j}}=\gamma_{ja}  \land \Pred_{OT_a}
       \land  
@@
  \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
-  \!\! ( \forall j\in J_a. \vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a} \land
+  \!\! ( \forall j\in J_a. \vis{\beta_{1j}}=\gamma_{ja}  \land \Pred_{OT_a} \land
      \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}) \wedge\\ \Pred_2\subst{\Post_1\uplus\Post_{OT_a}}  \\
@@
  \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
-\!\!   \left(\forall j\in J_a. \vis{\beta_{1j}}\!=\!\gamma_{ja}\Rightarrow \Pred_{OT_a}
+\!\!   \left(\forall j\in J_a. \vis{\beta_{1j}}\!=\!\gamma_{ja}\land \Pred_{OT_a}
      \!\land(\Pred_{s_{11},u_a}\wedge\Pred_2)\subst{\Post_1\uplus\Post_{OT_a}} \right)$\\
@@
  \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
-   \!\!(\forall j\in J_a. \vis{\beta_{1j}}\!\!=\!\gamma_{ja}  \Rightarrow \Pred_{OT_a}
+   \!\!(\forall j\in J_a. \vis{\beta_{1j}}\!\!=\!\gamma_{ja}  \land \Pred_{OT_a}
       \land (\displaystyle{\bigvee_{b\in B}}(
     \forall j\in J_{b}.
-\vis{\beta_{2j}}\!=\!\gamma_{jb}  \Rightarrow \Pred_{OT_{b}}\land \alpha'\!=\!\alpha_{2 b}\!
+\vis{\beta_{2j}}\!=\!\gamma_{jb}  \land \Pred_{OT_{b}}\land \\~\qquad\qquad\alpha'\!=\!\alpha_{2 b}\!
 \land \Pred_{s_{21},v_{b}}\subst{\Post_2\uplus\Post_{OT_{b}}})\subst{\Post_1\uplus\Post_{OT_a}})$\\
@@
 \vis{\beta_{1j}}\!\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-(\vis{\beta_{2j}}\!=\!\gamma_{jb})\subst{\Post_1\uplus\Post_{OT_a}}   \Rightarrow\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_1\uplus\Post_{OT_a}} \land  (\alpha'\!=\!\alpha_{2 b}) \subst{\Post_1\uplus\Post_{OT_a}} \land \\ \Pred_{s_{21},v_{b}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
+(\vis{\beta_{2j}}\!=\!\gamma_{jb})\subst{\Post_1\uplus\Post_{OT_a}}   \land\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_1\uplus\Post_{OT_a}} \land  (\alpha'\!=\!\alpha_{2 b}) \subst{\Post_1\uplus\Post_{OT_a}} \land \\ \Pred_{s_{21},v_{b}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
 Since $Post_1$  does not act on $\gamma_{jb}$, nor on $ \Pred_{OT_{b}}$ and $  \alpha_{2}$.
@@
 \vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-\vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jb} \subst{\Post_{OT_a}}  \Rightarrow\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_{OT_a}} \land \alpha'\subst{\Post_1}=\alpha_{2 b} \subst{\Post_{OT_a}} \land \Pred_{s_{21},v_b}\\\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
+\vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jb} \subst{\Post_{OT_a}}  \land\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_{OT_a}} \land \alpha'\subst{\Post_1}=\alpha_{2 b} \subst{\Post_{OT_a}} \land \Pred_{s_{21},v_b}\\\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
 Finally, the conjunction with the term $\Pred_3\subst{\Post_2\shortotimes\Post_1}$ of the both sides of the implication and rewriting, we get:\\
@@
 (\forall j\in J_a.\vis{\beta^1_j}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-\vis{\beta_{2j}}\subst{\Post_1}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}\Rightarrow \Pred_{OT_a}\land\Pred_{OT_{b}}\subst{\Post_{OT_a}} \land  \alpha'\subst{\Post_1}= \alpha_{2 b} \subst{\Post_{OT_a}} \land (\Pred_{s_{21},v_b} \land  \Pred_3)\\ \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{b}}\shortotimes\Post_{OT_a}})$\\
+\vis{\beta_{2j}}\subst{\Post_1}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}\land \Pred_{OT_a}\land\Pred_{OT_{b}}\subst{\Post_{OT_a}} \land  \alpha'\subst{\Post_1}= \alpha_{2 b} \subst{\Post_{OT_a}} \land (\Pred_{s_{21},v_b} \land  \Pred_3)\\ \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{b}}\shortotimes\Post_{OT_a}})$\\
 Again note that because of the domain  of the substitution is independent from some predicates and expressions, we removed $\Post_1$ and  we  added the term $\Post_{OT_{b}}\shortotimes\,\Post_{OT_a}$ in the substitution of the right side of the implication.\\
@@
 (\forall\! j\in\! J_a.\vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \!\in\! J_{b}.\vis{\beta_{2j}\subst{\Post_{OT_a}}}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}  \land 
- \forall j\!\in\! J_{c}. \vis{\beta_{3j} \subst{\Post_2\,\shortotimes\,\Post_1}} \!=\!\gamma_{jc} \subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}  \Rightarrow\\
+ \forall j\!\in\! J_{c}. \vis{\beta_{3j} \subst{\Post_2\,\shortotimes\,\Post_1}} \!=\!\gamma_{jc} \subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}  \land\\
    \underbrace{\Pred_{OT_a}\land\Pred_{OT_{b}} \subst{\Post_{OT_a}} \land 
@@
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}} \displaystyle{\bigvee_{b\in B}} \displaystyle{\bigvee_{c\in C}} 
-(\forall j\in J.\gamma_j'=\gamma_j \Rightarrow  \Pred \land \alpha=\alpha''  \land \Pred_{s',w_{c}}\subst{\Post_{OT}\uplus\Post\,}$\\
+(\forall j\in J.\gamma_j'=\gamma_j \land  \Pred \land \alpha=\alpha''  \land \Pred_{s',w_{c}}\subst{\Post_{OT}\uplus\Post\,}$\\
 
@@
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} 
-(\forall j\in J.\gamma_j'=\gamma_j \Rightarrow  \Pred \land \alpha=\alpha''  \land \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,}$\\
+(\forall j\in J.\gamma_j'=\gamma_j \land  \Pred \land \alpha=\alpha''  \land \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,}$\\
 \qed

### 2019-10-10 2016-Weak-FH-Bisim/WeakBisim.tex
work with rabea: sec 5

@@
 In the same manner, $\Pred_3$ must be applied the joint substitution $\Post_2\bigotimes\Post_1$.
-Similarly, effects on variables must be applied to obtain the global effect of the composed weak open transition, it must also be applied to observable actions of the holes, and to the global action of the weak open transition.
+Similarly, effects on variables must be applied to obtain the global effect of the composed weak open transition, it must also be applied to observable actions of the holes, and to the global action of the weak open transition	.
 

### 2019-10-16 2016-Weak-FH-Bisim/WeakBisim.tex
proof of thm 11

@@
  \begin{proof}  (Sketch of proof) Consider $Q$ weak FH-bisimilar to $Q'$.
-It means, according to Lemma  \ref{lem-alternative-weak-bisim} for any weak open transition $WOT$ in $Q$ there exist a family of weak open transitions $WOT_{x}^{x \in X}$ in $Q'$.
-We apply  Lemma \ref{lem-Weakcompose1} on weak open transition $WOT$, $j_0 \in J$, we obtain a new weak open transition $WOT'$ in $P[Q]_{j_0}$.
-On other hand, we apply same Lemma \ref{lem-Weakcompose1} on each weak open transitions $WOT_{x}$, so we obtain a new family of weak open transitions $WOT_{x}'$ in $P[Q']_{j_0}$.
-
-Suppose we have:\\[-2ex]
+It means, there exist a FH-bisimulation $\mathcal{R}_{Q,Q'}$ relating the two pNets $Q$ and $Q'$.
+We define a relation $\mathcal{R}$ relating states of $P[Q]_{j_0}$ with states of $P[Q']_{j_0}$:
+\[\mathcal{R} = \{(\ostate{S_P\uplus S_Q},\ostate{S_P\uplus S'_Q}, \Pred_{Q,Q'})|\,(s_Q,s_{Q'}, \Pred_{Q,Q'})\in\mathcal{R}_{Q,Q'}\}\]
+
+To prove weak FH-bisimulation of $\pNet[\pNetQ]_{j_0}$ and 
+	$\pNet[\pNetQ']_{j_0}$, we consider  an open transition of $\pNet[\pNetQ]_{j_0}$, and an equivalent state of $\pNet[\pNetQ']_{j_0}$, and we try to find a family of WOT of 	$\pNet[\pNetQ']_{j_0}$ that simulates it.
+Consider an OT of  $\pNet[\pNetQ]_{j_0}$ it is of the form (notations introduced to prepare the decomposition):
+\[
+\pNet[\pNetQ]_{j_0}\models\openrule
+	{
+		\beta_j^{j\in( J_P\uplus J_Q)}, 
+		\Pred_P\land \Pred_Q,  
+		\Post_P\uplus \Post_Q}
+	{\ostate{S_P\uplus S_Q} \OTWeakarrow {\alpha}
+		\ostate{S'_P\uplus S'_Q}
+}
+\]
+
+By the decomposition lemma for OTs (Lemma~\ref{lem-decompose}), we obtain the 2 following OTs (equality side-conditions have been inlined for clarity):
 \begin{mathpar}
 %\[
-P\models{\openrule
-	{
-		\beta_j^{j\in J}, 
-		\Pred,  
-		\Post}
-	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
-		\ostate{(s_i')^{\, i\in L}}}
+\pNet\models{\openrule
+	{
+		\beta_j^{j\in J_P}\uplus(j_0\mapsto \alpha_Q), 
+		\Pred_P,  
+		\Post_Q}
+	{\ostate{S_P} \OTWeakarrow {\alpha}
+		\ostate{S'_P}}
 }
@@
 	{
-		\set{\gamma},
+		\beta_j^{j\in J_Q},
 		 \Pred_Q,  
 		\Post_Q}
-	{\ostate{s_{i}^{i\in L_Q}} \OTWeakarrow {\alpha_Q}
-		\ostate{(s'_{i})^{\, i\in L_Q}}}
+	{\ostate{S_Q} \OTWeakarrow {\alpha_Q}
+		\ostate{S'_Q}}
 }%\]
@@
 
-Then, we have by lemma \ref{lem-Weakcompose}: \\[-2ex]
-	\[ P[Q]_{j_0}  
-	\models
-	{\openrule
-		{
-			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
-			\Pred\,',  \Post\,'
-			 }
-		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
-			\ostate{(s_i')^{\, i\in L\uplus L_Q}}}
-	}
-	\]
-
-On the other hand, $Q$ weak FH-bisimilar to $Q'$, so according to  Lemma  \ref{lem-alternative-weak-bisim} there exist a family of weak open transitions $WOT_{x}$:
+By definition of $\mathcal{R}$ we have 
+$(s_Q,s_{Q'}, \Pred_{Q,Q'})\in\mathcal{R}_{Q,Q'}$. And thus, by definition of weak FH-bisimulation, there exist a family of weak open transitions $WOT_{x}$:
  \begin{mathpar}
@@
          {
-           \gamma_{j x}^{j\in J_{x}}, \Pred_{Q_x},\Post_{Q_x}}
-         {\ostate{t_{i}^{i\in L_{Q_x}}}\OTWeakarrow {\alpha_x} \ostate{t_{ix}^{i\in L_{Q_x}}}}
+           \gamma_{j x}^{j\in J_Q}, \Pred_{Q' x},\Post_{Q' x}}
+         {\ostate{S_{Q'}}\OTWeakarrow {\alpha_{x}} \ostate{S'_{Q' x}}}
 \end{mathpar}
 
-such that...\\
-
-By applying  Lemma \ref{lem-Weakcompose} on each weak open transitions $WOT_{x}$, so we obtain a new family of weak open transitions $WOT_{x}'$ in $P[Q']_{j_0}$:
-
-\[ P[Q']_{j_0}  
-	\models
-	{\openrule
-		{
-			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
-			\Pred\,',  \Post\,'
-			 }
-		{\ostate{s_i^{i\in L} \uplus t_{i}^{i\in L_{Q_x}}} \OTWeakarrow {\alpha}
-			\ostate{(s_i')^{\, i\in L} \uplus t_{ix}^{i\in L_{Q_x}} }}
+where  
+\[\forall x.\, (S'_Q,S'_{Q' x}, \Pred_{Q,Q' x})\in\mathcal{R}_{Q,Q'}\]
+and
+\begin{equation*}
+\begin{split}
+\Pred_{Q,Q'}\land \Pred_Q \implies &
+\Big(\bigvee_{x\in X}
+(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x})\Rightarrow (\Pred_{Q_x}\land\\ &~~\alpha_Q=\alpha_x \land \Pred_{Q,Q' x}\subst{\Post_{Q' x}\uplus \Post_{Q}}) \Big)
+\end{split}
+\end{equation*}
+
+Composing the OT of $P$ with the WOTs of $Q'$ by Lemma~\ref{lem-Weakcompose1} we obtain:
+\[
+\pNet[\pNetQ']_{j_0}\models\openrule
+	{
+		\vis{\beta_j^{j\in( J_P}}\uplus\gamma_{j x}^{j\in J_Q}, 
+		\Pred_P\land \Pred_{Q' x},  
+		\Post_P\uplus \Post_{Q' x}}
+	{\ostate{S_P\uplus S_{Q'}} \OTWeakarrow {\alpha}
+		\ostate{S'_P\uplus S'_{Q' x}}
 }
 \]
+with $\alpha_Q=\alpha_x$
+
+Side conditions necessary to prove weak-FH bisimulations are:
+
+\[\forall x.\, (S'_P\uplus S'_Q,S'_P\uplus S'_{Q' x}, \Pred_{Q,Q' x})\in\mathcal{R}\]
+which is trivially verified, and
+\begin{equation*}
+\begin{split}
+\Pred_{Q,Q'}\land \Pred_P\land \Pred_Q \implies &
+\Big(\bigvee_{x\in X}
+(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x}\land \forall j\in J_P.\, \vis{\beta_j}=\vis{\beta_j}))\Rightarrow\\
+& (\Pred_P\land \Pred_{Q' x}\land\\ &~~\alpha=\alpha \land \Pred_{Q,Q' x}\subst{\Post_P\uplus\Post_{Q' x}\uplus \Post_{Q}}) \Big)
+\end{split}
+\end{equation*}
+We conclude by observing that $\Post_P$ has no effect on variables of $Q$ and $Q'$, and thus on $\Pred_{Q,Q' x}$
+\qed
+
+% OLD
+% according to Lemma  \ref{lem-alternative-weak-bisim} for any weak open transition $WOT$ in $Q$ there exist a family of weak open transitions $WOT_{x}^{x \in X}$ in $Q'$. 
+%We apply  Lemma \ref{lem-Weakcompose1} on weak open transition $WOT$, $j_0 \in J$, we obtain a new weak open transition $WOT'$ in $P[Q]_{j_0}$.
+%On other hand, we apply same Lemma \ref{lem-Weakcompose1} on each weak open transitions $WOT_{x}$, so we obtain a new family of weak open transitions $WOT_{x}'$ in $P[Q']_{j_0}$.
+%
+%Suppose we have:\\[-2ex]
+%\begin{mathpar}
+%%\[
+%P\models{\openrule
+%	{
+%		\beta_j^{j\in J}, 
+%		\Pred,  
+%		\Post}
+%	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
+%		\ostate{(s_i')^{\, i\in L}}}
+%}
+%\quad\text{~~and~~}\quad
+%Q\models{\openrule
+%	{
+%		\set{\gamma},
+%		 \Pred_Q,  
+%		\Post_Q}
+%	{\ostate{s_{i}^{i\in L_Q}} \OTWeakarrow {\alpha_Q}
+%		\ostate{(s'_{i})^{\, i\in L_Q}}}
+%}%\]
+%
+%
+%\end{mathpar}
+%
+%Then, we have by lemma \ref{lem-Weakcompose}: \\[-2ex]
+%	\[ P[Q]_{j_0}  
+%	\models
+%	{\openrule
+%		{
+%			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
+%			\Pred\,',  \Post\,'
+%			 }
+%		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
+%			\ostate{(s_i')^{\, i\in L\uplus L_Q}}}
+%	}
+%	\]
+%
+%On the other hand, $Q$ weak FH-bisimilar to $Q'$, so according to  Lemma  \ref{lem-alternative-weak-bisim} 
+%
+%such that...\\
+%
+%By applying  Lemma \ref{lem-Weakcompose} on each weak open transitions $WOT_{x}$, so we obtain a new family of weak open transitions $WOT_{x}'$ in $P[Q']_{j_0}$:
+%
+%\[ P[Q']_{j_0}  
+%	\models
+%	{\openrule
+%		{
+%			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
+%			\Pred\,',  \Post\,'
+%			 }
+%		{\ostate{s_i^{i\in L} \uplus t_{i}^{i\in L_{Q_x}}} \OTWeakarrow {\alpha}
+%			\ostate{(s_i')^{\, i\in L} \uplus t_{ix}^{i\in L_{Q_x}} }}
+%	}
+%	\]
 
@@
 \end{theorem}
-  \newpage
+
+\end{document}
 \section{Examples of Lotos laws}

### 2019-10-16 2016-Weak-FH-Bisim/WeakBisim.tex
type thm 11
typo
typos again

@@
 \end{theorem}
- \begin{proof}  (Sketch of proof) Consider $Q$ weak FH-bisimilar to $Q'$.
-It means, there exist a FH-bisimulation $\mathcal{R}_{Q,Q'}$ relating the two pNets $Q$ and $Q'$.
+ \begin{proof}  Consider $Q$ weak FH-bisimilar to $Q'$.
+It means that there exist a FH-bisimulation $\mathcal{R}_{Q,Q'}$ relating the two pNets $Q$ and $Q'$.
 We define a relation $\mathcal{R}$ relating states of $P[Q]_{j_0}$ with states of $P[Q']_{j_0}$:
-\[\mathcal{R} = \{(\ostate{S_P\uplus S_Q},\ostate{S_P\uplus S'_Q}, \Pred_{Q,Q'})|\,(s_Q,s_{Q'}, \Pred_{Q,Q'})\in\mathcal{R}_{Q,Q'}\}\]
+\[\mathcal{R} = \{(\ostate{S_P\uplus S_Q},\ostate{S_P\uplus S_{Q'}}, \Pred_{Q,Q'})|\,(S_Q,S_{Q'}, \Pred_{Q,Q'})\in\mathcal{R}_{Q,Q'}\}\]
 
 To prove weak FH-bisimulation of $\pNet[\pNetQ]_{j_0}$ and 
-	$\pNet[\pNetQ']_{j_0}$, we consider  an open transition of $\pNet[\pNetQ]_{j_0}$, and an equivalent state of $\pNet[\pNetQ']_{j_0}$, and we try to find a family of WOT of 	$\pNet[\pNetQ']_{j_0}$ that simulates it.
+	$\pNet[\pNetQ']_{j_0}$, we consider  an open transition $OT$ of $\pNet[\pNetQ]_{j_0}$, and an equivalent state of $\pNet[\pNetQ']_{j_0}$, and we try to find a family of WOT of 	$\pNet[\pNetQ']_{j_0}$ that simulates $OT$.
 Consider an OT of  $\pNet[\pNetQ]_{j_0}$ it is of the form (notations introduced to prepare the decomposition):
@@
 By definition of $\mathcal{R}$ we have 
-$(s_Q,s_{Q'}, \Pred_{Q,Q'})\in\mathcal{R}_{Q,Q'}$. And thus, by definition of weak FH-bisimulation, there exist a family of weak open transitions $WOT_{x}$:
+$(S_Q,S_{Q'}| \Pred_{Q,Q'})\in\mathcal{R}_{Q,Q'}$. And thus, by definition of weak FH-bisimulation, there exist a family of weak open transitions $WOT_{x}$:
  \begin{mathpar}
@@
 where  
-\[\forall x.\, (S'_Q,S'_{Q' x}, \Pred_{Q,Q' x})\in\mathcal{R}_{Q,Q'}\]
+\[\forall x.\, (S'_Q,S'_{Q' x}| \Pred_{Q,Q' x})\in\mathcal{R}_{Q,Q'}\]
 and
@@
 \]
-with $\alpha_Q=\alpha_x$
+with $\bigvee_{x\in X}
+(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x} \implies \alpha_Q=\alpha_x$ that ensures that the open transitions can be recomposed when the OT fires.
 
@@
 
-\[\forall x.\, (S'_P\uplus S'_Q,S'_P\uplus S'_{Q' x}, \Pred_{Q,Q' x})\in\mathcal{R}\]
+\[\forall x.\, (S'_P\uplus S'_Q,S'_P\uplus S'_{Q' x}| \Pred_{Q,Q' x})\in\mathcal{R}\]
 which is trivially verified, and
@@
 \end{theorem}
+
+ \begin{proof}   Consider $P$ weak FH-bisimilar to $P'$.
+It means, there exist a FH-bisimulation $\mathcal{R}_{P,P'}$ relating the two pNets $P$ and $P'$.
+We define a relation $\mathcal{R}$ relating states of $P[Q]_{j_0}$ with states of $P'[Q]_{j_0}$:
+\[\mathcal{R} = \{(\ostate{S_P\uplus S_Q},\ostate{S_{P'}\uplus S_Q}, \Pred_{P,P'})|\,(S_P,S_{P'}, \Pred_{P,P'})\in\mathcal{R}_{P,P'}\}\]
+
+To prove weak FH-bisimulation of $\pNet[\pNetQ]_{j_0}$ and 
+	$\pNet'[\pNetQ]_{j_0}$, we consider  an open transition $OT$ of $\pNet[\pNetQ]_{j_0}$, and an equivalent state of $\pNet'[\pNetQ]_{j_0}$, and we try to find a family of WOT of 	$\pNet'[\pNetQ]_{j_0}$ that simulates $OT$.
+Consider an OT of  $\pNet[\pNetQ]_{j_0}$ it is of the form (notations introduced to prepare the decomposition):
+\[
+\pNet[\pNetQ]_{j_0}\models\openrule
+	{
+		\beta_j^{j\in( J_P\uplus J_Q)}, 
+		\Pred_P\land \Pred_Q,  
+		\Post_P\uplus \Post_Q}
+	{\ostate{S_P\uplus S_Q} \OTWeakarrow {\alpha}
+		\ostate{S'_P\uplus S'_Q}
+}
+\]
+
+By the decomposition lemma for OTs (Lemma~\ref{lem-decompose}), we obtain the 2 following OTs (equality side-conditions have been inlined for clarity):
+\begin{mathpar}
+%\[
+\pNet\models{\openrule
+	{
+		\beta_j^{j\in J_P}\uplus(j_0\mapsto \alpha_Q), 
+		\Pred_P,  
+		\Post_Q}
+	{\ostate{S_P} \OTWeakarrow {\alpha}
+		\ostate{S'_P}}
+}
+\quad\text{~~and~~}\quad
+Q\models{\openrule
+	{
+		\beta_j^{j\in J_Q},
+		 \Pred_Q,  
+		\Post_Q}
+	{\ostate{S_Q} \OTWeakarrow {\alpha_Q}
+		\ostate{S'_Q}}
+}%\]
+
+\end{mathpar}
+
+By definition of $\mathcal{R}$ we have 
+$(S_P,S_{P'}, \Pred_{Q,Q'})\in\mathcal{R}_{Q,Q'}$. And thus, by definition of weak FH-bisimulation, there exist a family of weak open transitions $WOT_{x}$:
+ \begin{mathpar}
+    \openrule
+         {
+           \gamma_{j x}^{j\in J_Q}, \Pred_{Q' x},\Post_{Q' x}}
+         {\ostate{S_{Q'}}\OTWeakarrow {\alpha_{x}} \ostate{S'_{Q' x}}}
+\end{mathpar}
+
+where  
+\[\forall x.\, (S'_Q,S'_{Q' x}, \Pred_{Q,Q' x})\in\mathcal{R}_{Q,Q'}\]
+and
+\begin{equation*}
+\begin{split}
+\Pred_{Q,Q'}\land \Pred_Q \implies &
+\Big(\bigvee_{x\in X}
+(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x})\Rightarrow (\Pred_{Q_x}\land\\ &~~\alpha_Q=\alpha_x \land \Pred_{Q,Q' x}\subst{\Post_{Q' x}\uplus \Post_{Q}}) \Big)
+\end{split}
+\end{equation*}
+
+Composing the OT of $P$ with the WOTs of $Q'$ by Lemma~\ref{lem-Weakcompose1} we obtain:
+\[
+\pNet[\pNetQ']_{j_0}\models\openrule
+	{
+		\vis{\beta_j^{j\in( J_P}}\uplus\gamma_{j x}^{j\in J_Q}, 
+		\Pred_P\land \Pred_{Q' x},  
+		\Post_P\uplus \Post_{Q' x}}
+	{\ostate{S_P\uplus S_{Q'}} \OTWeakarrow {\alpha}
+		\ostate{S'_P\uplus S'_{Q' x}}
+}
+\]
+with $\alpha_Q=\alpha_x$
+
+Side conditions necessary to prove weak-FH bisimulations are:
+
+\[\forall x.\, (S'_P\uplus S'_Q,S'_P\uplus S'_{Q' x}, \Pred_{Q,Q' x})\in\mathcal{R}\]
+which is trivially verified, and
+\begin{equation*}
+\begin{split}
+\Pred_{Q,Q'}\land \Pred_P\land \Pred_Q \implies &
+\Big(\bigvee_{x\in X}
+(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x}\land \forall j\in J_P.\, \vis{\beta_j}=\vis{\beta_j}))\Rightarrow\\
+& (\Pred_P\land \Pred_{Q' x}\land\\ &~~\alpha=\alpha \land \Pred_{Q,Q' x}\subst{\Post_P\uplus\Post_{Q' x}\uplus \Post_{Q}}) \Big)
+\end{split}
+\end{equation*}
+We conclude by observing that $\Post_P$ has no effect on variables of $Q$ and $Q'$, and thus on $\Pred_{Q,Q' x}$
+\qed
+\end{proof}
 

### 2019-10-16 2016-Weak-FH-Bisim/WeakBisim.tex
proof thm 12

@@
 By definition of $\mathcal{R}$ we have 
-$(S_P,S_{P'}, \Pred_{Q,Q'})\in\mathcal{R}_{Q,Q'}$. And thus, by definition of weak FH-bisimulation, there exist a family of weak open transitions $WOT_{x}$:
+$(S_P,S_{P'}, \Pred_{P,P'})\in\mathcal{R}_{P,P'}$. And thus, by definition of weak FH-bisimulation, there exist a family of weak open transitions $WOT_{x}$:
  \begin{mathpar}
@@
          {
-           \gamma_{j x}^{j\in J_Q}, \Pred_{Q' x},\Post_{Q' x}}
-         {\ostate{S_{Q'}}\OTWeakarrow {\alpha_{x}} \ostate{S'_{Q' x}}}
+           \gamma_{j x}^{j\in J_P\uplus\{j_0\}}, \Pred_{P' x},\Post_{P' x}}
+         {\ostate{S_{P'}}\OTWeakarrow {\alpha_{x}} \ostate{S'_{P' x}}}
 \end{mathpar}
@@
 where  
-\[\forall x.\, (S'_Q,S'_{Q' x}, \Pred_{Q,Q' x})\in\mathcal{R}_{Q,Q'}\]
+\[\forall x.\, (S'_P,S'_{P' x}, \Pred_{P,P' x})\in\mathcal{R}_{P,P'}\]
 and
@@
 \begin{split}
-\Pred_{Q,Q'}\land \Pred_Q \implies &
+\Pred_{P,P'}\land \Pred_P \implies &
 \Big(\bigvee_{x\in X}
-(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x})\Rightarrow (\Pred_{Q_x}\land\\ &~~\alpha_Q=\alpha_x \land \Pred_{Q,Q' x}\subst{\Post_{Q' x}\uplus \Post_{Q}}) \Big)
+(\forall j\in J_P.\, \vis{\beta_j}=\gamma_{j x} \land \vis{\alpha_Q}=\gamma_{j_0})\Rightarrow (\Pred_{Q_x}\land\\ &~~\alpha=\alpha_x \land \Pred_{P,P' x}\subst{\Post_{P' x}\uplus \Post_{P}}) \Big)
 \end{split}
@@
 
-Composing the OT of $P$ with the WOTs of $Q'$ by Lemma~\ref{lem-Weakcompose1} we obtain:
+We here need a special case of Lemma\ref{lem-Weakcompose}where the inner pNet $Q$ does a simple OT.
+This is just a particular case of the theorem but where notations get simplified because the inner pnet does a single transition.
+ This way we can compose the WOTs of $P'$ with the OT of $Q$ and obtain, whenever $\vis{\beta_j}=\gamma_{j x} $:
 \[
-\pNet[\pNetQ']_{j_0}\models\openrule
-	{
-		\vis{\beta_j^{j\in( J_P}}\uplus\gamma_{j x}^{j\in J_Q}, 
-		\Pred_P\land \Pred_{Q' x},  
-		\Post_P\uplus \Post_{Q' x}}
-	{\ostate{S_P\uplus S_{Q'}} \OTWeakarrow {\alpha}
-		\ostate{S'_P\uplus S'_{Q' x}}
+\pNet'[\pNetQ]_{j_0}\models\openrule
+	{
+		\vis{\beta_j^{j\in( J_Q}}\uplus\gamma_{j x}^{j\in J_Q}, 
+		\Pred_{P' x}\land \Pred_Q,  
+		\Post_{P' x}\uplus \Post_Q}
+	{\ostate{S_{P'}\uplus S_{Q}} \OTWeakarrow {\alpha_x}
+		\ostate{{S'_{P' x}}\uplus S'_Q}
 }
 \]
-with $\alpha_Q=\alpha_x$
-
 Side conditions necessary to prove weak-FH bisimulations are:
 
-\[\forall x.\, (S'_P\uplus S'_Q,S'_P\uplus S'_{Q' x}, \Pred_{Q,Q' x})\in\mathcal{R}\]
+\[\forall x.\, (S'_P\uplus S'_Q,S'_{P' x}\uplus S'_Q, \Pred_{P,P' x})\in\mathcal{R}\]
 which is trivially verified, and
@@
 \begin{split}
-\Pred_{Q,Q'}\land \Pred_P\land \Pred_Q \implies &
+\Pred_{P,P'}\land \Pred_P\land \Pred_Q \implies &
 \Big(\bigvee_{x\in X}
-(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x}\land \forall j\in J_P.\, \vis{\beta_j}=\vis{\beta_j}))\Rightarrow\\
-& (\Pred_P\land \Pred_{Q' x}\land\\ &~~\alpha=\alpha \land \Pred_{Q,Q' x}\subst{\Post_P\uplus\Post_{Q' x}\uplus \Post_{Q}}) \Big)
+(\forall j\in J_P.\, \vis{\beta_j}\gamma_{j x} \land \forall j\in J_Q.\, \vis{\beta_j}=\vis{\beta_j} )\Rightarrow\\
+& (\Pred_{P' x}\land \Pred_Q\land\\ &~~\alpha_x=\alpha \land \Pred_{P,P' x}\subst{\Post_{P' x}\uplus\Post_P\uplus \Post_{Q}}) \Big)
 \end{split}
 \end{equation*}
-We conclude by observing that $\Post_P$ has no effect on variables of $Q$ and $Q'$, and thus on $\Pred_{Q,Q' x}$
+We conclude by observing that $\Post_Q$ has no effect on variables of $P$ and $P'$, and thus on $\Pred_{P,P' x}$
 \qed

### 2019-10-16 2016-Weak-FH-Bisim/WeakBisim.tex
notation revision

--- 2019-10-16 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 predicate for the open 
-transition is: $\displaystyle{\Pred\,''=\!\!\!\!\bigwedge_{m\in I _1\uplus I_2}\!\!\!\Pred_m \land \Pred\,'
+transition is:\\
+ $\displaystyle{\Pred\,''=\!\!\!\!\bigwedge_{m\in I _1\uplus I_2}\!\!\!\Pred_m \land \Pred\,'
 \land \Pred(SV_k,v_i^{i\in I_1\uplus I_2}\uplus(j_0\mapsto v_Q),\beta_j^{j\in 
-J},\alpha)}$. 
-By definition 
+J},\alpha)}$. \\
+By definition we have:\\
 $\Pred(SV_k,\alpha_i^{i\in I}\uplus(j_0\mapsto \alpha_Q),\beta_j^{j\in 
@@
 	the leaves: $\displaystyle{\biguplus_{m\in I_1\cup\{j_0\}\uplus I_2} 
-    		\!\!\!\!\!\Post_m = 	\Post\uplus \Post\,'}$. Finally, the composed open transition can be
+    		\!\!\!\!\!\Post_m = 	\Post\uplus \Post\,'}$.\\ Finally, the composed open transition can be
         built by \TrDeux:
@@
  t=t'\uplus s'' \land s''\in \mathcal{S}_P \land (s',t'|\Pred_{s,t})\in\mathcal{R}\}$ 
-
- where $\mathcal{S}_S$ is the set of states of the open automaton of $P$.	We will prove 
+   where $\mathcal{S}_P$ is the set of states of the open automaton of $P$.	We will prove 
  that $\mathcal{R}'$ is an open FH-bisimulation. Consider a pair of FH-bisimilar 
@@
  $\Pred_{s,t} \land \Pred\,''
- \Rightarrow \displaystyle{\bigvee_{x\in X}
- \left( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \land 
+ \implies$\\ $\displaystyle{\bigvee_{x\in X}
+ \left( \forall j\in J\cap \Holes(Q). \beta_j\!=\!\beta_{jx}\!  \land\! 
  \Pred_{OT_x}
  \land \alpha_Q\!=\!\alpha_x \land  
- \Pred_{s x}\subst{\Post\,''\uplus\Post_{OT_x}}\right)}$
+ \Pred_{s, x}\subst{\Post\,''\uplus\Post_{OT_x}}\right)}$
 
@@
  FH-bisimulation between $OT$ and $OT_x$.
- $\forall x, (\ostate{{s'}_{i}^{~i\in L_P\uplus L}},\ostate{t_{i 
- 		x}^{i\in L_P\uplus L'}}|\Pred_{s x})\in 
+ $\forall x, (\ostate{{s'}_{i}^{~i\in L_P\uplus L}},\ostate{t_{i 	x}^{i\in L_P\uplus L'}}|\Pred_{s, x})\in 
  \mathcal{R}'$ (by definition of
@@
  \noindent                        
- \begin{small} $\Pred_{s,t} \land \Pred_{OT} \implies
- 	\Pred_{s,t}\land\Pred\,'\land \Pred\,''\land\alpha_Q=\beta_{j_0}\\ % 
+ \begin{small} $\Pred_{s,t} \land \Pred_{OT}\\ 
+ \implies 	\Pred_{s,t}\land\Pred\,'\land \Pred\,''\land\alpha_Q=\beta_{j_0}\\ % 
  	%reversed 
@@
  	\land \alpha_Q\!=\!\alpha_x \land  
- 	\Pred_{s x}\subst{\Post\,''\uplus\Post_{OT_x}}\right)
- }
- \\~\qquad\qquad	\land \Pred\,'\land\alpha_Q=\beta_{j_0} \\
+ 	\Pred_{s x}\subst{\Post\,''\uplus\Post_{OT_x}}\right)\land
+ }
+ \\~\qquad\quad \Pred\,'\land\alpha_Q=\beta_{j_0} \\
  	\implies
@@
  	{\displaystyle\bigvee_{x\in X}
- 		\left( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \land 
+ 		( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \land 
  		\Pred\,'\land \Pred_{OT_x}
- 		\land \alpha_Q\!=\!\alpha_x \land \alpha_Q\!=\!\beta_{j_0 x} \land  
- 		\Pred_{s x}\subst{\Post\,''\uplus\Post_{OT_x}}\right)
- 	}
+ 		\land \alpha_Q\!=\!\alpha_x \land \alpha_Q\!=\!\beta_{j_0 x}\, \land} \\ 
+ 	~\qquad\quad 	\Pred_{s, x}\subst{\Post\,''\uplus\Post_{OT_x}})
  	 $\end{small}
+
  Note that, $\beta_{j_0}$ can be transformed into  $\beta_{j_0 x}$ because of the 
@@
  	adding prerequisite on more variables 
- 	does not 
- 	change the validity of the formula (those variables are not used).
+ 	does not   	change the validity of the formula (those variables are not used).
  	\item Concerning the last term, we need 
- 	$\Pred_{s x}\subst{\Post_{OT}\uplus(\Post\,'\uplus \Post_{OT_x})}$ 
- 	, i.e.:
- 	$\Pred_{s x}\subst{(\Post\,'\uplus 
- 		\Post\,'')\uplus(\Post\,'\uplus \Post_{OT_x})}$. We 
+ 	$\Pred_{s x}\subst{\Post_{OT}\uplus(\Post\,'\uplus \Post_{OT_x})}$, i.e.
+ 	$\Pred_{s x}\subst{(\Post\,'\uplus 	\Post\,'')\uplus(\Post\,'\uplus \Post_{OT_x})}$. We 
  	can conclude by observing that	$\Pred_{s x}$ does not use any variable of $P$ 
@@
  \end{itemize}	
-Finally: 
-\[{\displaystyle\bigvee_{x\in X}
- 		\left( \forall j\in J. \beta_j=\beta_{jx}  \land 
- 		\left(\Pred\,'\land \Pred_{OT_x}
- 		 \land \alpha_Q\!=\!\beta_{j_0 x}\right) \land \alpha_Q\!=\!\alpha_x\land  
- 		\Pred_{s x}\subst{\Post\,''\uplus\Post_{OT_x}}\right)
- 	}\]
+Finally: \\
+\begin{small} $\Pred_{s,t} \land \Pred_{OT} \implies\\
+{\displaystyle\bigvee_{x\in X}
+ 		\!\left( \forall j\in J. \beta_j=\beta_{jx} \! \land\! 
+ 		\big(\Pred\,'\land\! \Pred_{OT_x}
+ 		 \land \alpha_Q\!=\!\beta_{j_0 x}\right)\! \land\! \alpha_Q\!=\!\alpha_x\land\!  \Pred_{s, x}\subst{\Post\,''\!\uplus\!\Post_{OT_x}}\big)
+ 		}$
+ 		\end{small}\\
 This proves the  condition of the FH-simulation, the other direction is 
@@
 			$\displaystyle{\Pred_{s,t} \land \Pred\,'
-		 \Rightarrow \bigvee_{x\in X}
-			\left( \forall j\in J'. \beta_j=\beta_{jx}  \land 
-			\Pred_{OT_x}
-			\land \alpha\!=\!\alpha_x \land  
-			\Pred_{s x}\subst{\Post\,'\uplus\Post_{OT_x}}\right)}$
+		 \!\!\implies\!\!\! \bigvee_{x\in X}\!
+			\left( \forall j\in J'. \beta_j=\beta_{jx}\!  \land\! 
+			\Pred_{OT_x}\!
+			\land\! \alpha\!=\!\alpha_x\! \land\!  
+			\Pred_{s,x}\subst{\Post\,'\uplus\Post_{OT_x}}\right)}$
 			%     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x}) \right)$.
@@
 			FH-bisimulation between $OT$ and $OT_x$.
-
 			 $\forall x, (\ostate{{s'}_{i}^{~i\in L\uplus L_Q}},\ostate{t_{i 
-			x}^{~i\in L'\uplus L_Q}}|\Pred_{s x})\in 
+			x}^{~i\in L'\uplus L_Q}}|\Pred_{s, x})\in 
 			\mathcal{R}'$ (by definition of
@@
 \noindent                        
-\begin{small} $\Pred_{s,t} \land \Pred_{OT} \implies
+\begin{small} 
+$\Pred_{s,t} \land \Pred_{OT}\\ \implies
  \Pred_{s,t}\land\Pred\,'\land \Pred\,''\land \alpha_Q=\beta_{j_0}\\  
@@
 {\displaystyle{\bigvee_{x\in X}\!(\forall j\!\in\! J'. \beta_j\!=\!\beta_{jx}  
-\land \!
-\Pred_{OT_x}\land \alpha_Q=\beta_{j_0}
-\land \alpha\!=\!\alpha_x}} %\\ \hspace*{40mm} %
-\land \Pred_{s x}\subst{\Post\,'\uplus\Post_{OT_x}}) \land
+\!\land \!
+\Pred_{OT_x}\!\land\! \alpha_Q\!=\!\beta_{j_0}
+\land\! \alpha\!=\!\alpha_x}} %\\ \hspace*{40mm} %
+\land \Pred_{s, x}\subst{\Post\,'\uplus\Post_{OT_x}}) \land
 \Pred\,''\\ % 
@@
 \land \!
-\left(\Pred_{OT_x}\land
-\Pred\,''
+\left(\Pred_{OT_x}\!\land\!
+\Pred\,''\!
 \land \alpha_Q\!=\!\beta_{j_0 x}\right)
@@
 	\item We need $\Pred_{s x}\subst{\Post_{OT}\uplus(\Post_{OT_x}\uplus \Post\,'')}$, i.e.:
-	$\Pred_{s x}\subst{(\Post\,'\uplus \Post\,'')\uplus(\Post_{OT_x}\uplus \Post\,'')}$. We 
+	$\Pred_{s,x}\subst{(\Post\,'\uplus \Post\,'')\uplus(\Post_{OT_x}\uplus \Post\,'')}$. We 
 	can conclude by observing that	$\Pred_{s x}$ does not use any variable of $Q$ 
@@
 
-We  define a quantified composition operator for effects, i.e.$\Post$ elements of the open transitions.
+We  define a quantified composition operator for effects, i.e. $\Post$ elements of the open transitions.
 We use ${\displaystyle \bigotimes_{i=n}^{0} \Post_i}$ to denote  $\Post_n\otimes .. \otimes \Post_0$. By convention ${\displaystyle \bigotimes_{i=-1}^{0} \Post_i}$ is the identity.
@@
 \displaystyle{
-\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
+\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup}\\
+~\qquad \displaystyle{\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
 \\
@@
 \displaystyle{
-\set{\gamma}=\mybigdotcup_{i=1}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
+\set{\gamma}=\mybigdotcup_{i=1}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup}\\
+~\qquad \displaystyle{\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
 \\
@@
            \vis{\set{\beta_{10}}}\!,\Pred_{10},\Post_{10}
-				 } {s_{10} \OTWeakarrow {\tau}s_{11}} \in \WT
-\qquad
+				 } {s_{10} \OTWeakarrow {\tau}s_{11}} \in\! \WT
+\quad
 \openrule
@@
 		\Pred, \Post
-				 } {s'' \OTWeakarrow {\alpha'} s'} \in\WT
-\qquad
+				 } {s'' \OTWeakarrow {\alpha'} s'} \in\!\WT
+\quad
 \openrule
@@
           \emptyset,\True,\Id(s'')
-				 } {s' \OTWeakarrow {\tau} s'} \in \WT
+				 } {s' \OTWeakarrow {\tau} s'} \in\! \WT
 \\
@@
 				 } 
-         {s_{10} \OTWeakarrow {\alpha''} s'} \in\WT
+         {s_{10} \OTWeakarrow {\alpha''} s'} \in\!\WT
 } \WTTrois
@@
 \displaystyle{
-\set{\gamma''}=\mybigdotcup_{i=0}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
+\set{\gamma''}=\mybigdotcup_{i=0}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup}\\
+~\qquad~\displaystyle{ \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
 \\
@@
 				 } {s \OTWeakarrow {\tau} s}\! \in\! \WT
-}\!\! \implies\!\! \Big(\alpha = \tau \wedge \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
+}\!\! \Rightarrow\!\! \Big(\alpha = \tau \wedge \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
 $
@@
            \set{\gamma},\Pred,\Post}
-         {s \OTWeakarrow {\alpha} s'} \in \WT \implies
+         {s \OTWeakarrow {\alpha} s'} \in \WT \Rightarrow
          \openrule
@@
          {s \OTWeakarrow {\tau} s'} \in\! \WT 
-\implies 
+\Rightarrow \,
  \forall i \in [0..n_1].\openrule
@@
          {s'' \OTWeakarrow {\tau} s'''} \in\! \WT
-\implies 
+\Rightarrow\, 
 \forall i \in [0..m_1].\openrule
@@
          {s' \OTWeakarrow {\alpha'} s''} \in\! \WT
-\implies 
+\Rightarrow 
 \bigg(\forall i \in [0..n_2].\openrule
@@
 \displaystyle{
-\set{\gamma_2}=\mybigdotcup_{i=0}^{n_2} \vis{\set{\beta_{2i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{2 j} } }  \dotcup  \vis{\set{\beta'}\subst{\bigotimes_{j=n_2}^{0}\Post_{2j}}} }\\~\qquad
-\dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{2i}} \subst{\bigotimes_{j=i-1}^{0}\Post'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j=n_2}^{0}\Post_{2j}} }
+\set{\gamma_2}=\mybigdotcup_{i=0}^{n_2} \vis{\set{\beta_{2i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{2 j} } }  \dotcup  \vis{\set{\beta'}\subst{\bigotimes_{j=n_2}^{0}\Post_{2j}}} \dotcup}\\~\qquad
+ \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{2i}} \subst{\bigotimes_{j=i-1}^{0}\Post'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j=n_2}^{0}\Post_{2j}} }
 \\
@@
 }
- \implies
+ \Rightarrow
 \bigg(\forall i\in [0..(n_1\!+\!n_2)].\openrule
@@
 ~~\\
-\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2} \vis{\set{\beta_{4i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{4 j} } }  \dotcup  \vis{\set{\beta'}\subst{\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}}}\\~\qquad
-\dotcup\!\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta_{5i}}\subst{\bigotimes_{j=i-1}^{0}\Post'_{5i}\shortotimes\Post\,'\shortotimes\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4i}} }
+\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2} \vis{\set{\beta_{4i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{4 j} } }  \dotcup  \vis{\set{\beta'}\subst{\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}}\dotcup }\\~\!\qquad\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta_{5i}}\subst{\bigotimes_{j=i-1}^{0}\Post'_{5i}\shortotimes\Post\,'\shortotimes\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4i}} }
 \\
@@
 \displaystyle{\implies\!\!\! \bigvee_{x\in X}
-   \left( \forall j\in J_x.\gamma_j=\gamma_{jx}  \land \Pred_{OT_x}
-     \land \alpha\!=\!\alpha_x \land  
+   \left( \forall j\in J_x.\gamma_j\!=\!\gamma_{jx}\!\land\! \Pred_{OT_x}
+     \land \alpha\!=\!\alpha_x \!\land\!  
      \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}$
@@
 \displaystyle{
-\gamma_j^{j\in J'}=\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
+\gamma_j^{j\in J'}=\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup}\\
+~\qquad\qquad\!\displaystyle{\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
 \\
 \Pred_{OT}=\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=n}^{0}\Post_{1j}}\land\\ 
-~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}}\Big)\\
+~\qquad\qquad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}}\Big)\\
 \Post_{OT}=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}$
@@
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
-  \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}=\gamma_{ja}  \land \Pred_{OT_a}
-     \land \alpha_{1 a}\!=\!\tau \land  
+  \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}\!=\!\gamma_{ja} \!\land\! \Pred_{OT_a}\!
+     \land\! \alpha_{1 a}\!=\!\tau \land  
      \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$
@@
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{b\in B}}
- \!\!  \left( \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}\land \Pred_{OT_{b}}\!\land \alpha'\!=\!\alpha_{2 b} \land  
+ \!\!  \left( \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}\land \Pred_{OT_{b}}\!\land \alpha'\!=\!\alpha_{2 b}\! \land\!  
      \Pred_{s_{21},v_{b}}\subst{\Post_2\uplus\Post_{OT_{b}}}\right)$
@@
  \begin{proof}  (Sketch of proof) Consider $Q$ weak FH-bisimilar to $Q'$.
-It means, there exist a FH-bisimulation $\mathcal{R}_{Q,Q'}$ relating the two pNets $Q$ and $Q'$.
-We define a relation $\mathcal{R}$ relating states of $P[Q]_{j_0}$ with states of $P[Q']_{j_0}$:
-\[\mathcal{R} = \{(\ostate{S_P\uplus S_Q},\ostate{S_P\uplus S'_Q}, \Pred_{Q,Q'})|\,(s_Q,s_{Q'}, \Pred_{Q,Q'})\in\mathcal{R}_{Q,Q'}\}\]
-
-To prove weak FH-bisimulation of $\pNet[\pNetQ]_{j_0}$ and 
-	$\pNet[\pNetQ']_{j_0}$, we consider  an open transition of $\pNet[\pNetQ]_{j_0}$, and an equivalent state of $\pNet[\pNetQ']_{j_0}$, and we try to find a family of WOT of 	$\pNet[\pNetQ']_{j_0}$ that simulates it.
-Consider an OT of  $\pNet[\pNetQ]_{j_0}$ it is of the form (notations introduced to prepare the decomposition):
-\[
-\pNet[\pNetQ]_{j_0}\models\openrule
-	{
-		\beta_j^{j\in( J_P\uplus J_Q)}, 
-		\Pred_P\land \Pred_Q,  
-		\Post_P\uplus \Post_Q}
-	{\ostate{S_P\uplus S_Q} \OTWeakarrow {\alpha}
-		\ostate{S'_P\uplus S'_Q}
-}
-\]
-
-By the decomposition lemma for OTs (Lemma~\ref{lem-decompose}), we obtain the 2 following OTs (equality side-conditions have been inlined for clarity):
+It means, according to Lemma  \ref{lem-alternative-weak-bisim} for any weak open transition $WOT$ in $Q$ there exist a family of weak open transitions $WOT_{x}^{x \in X}$ in $Q'$.
+We apply  Lemma \ref{lem-Weakcompose1} on weak open transition $WOT$, $j_0 \in J$, we obtain a new weak open transition $WOT'$ in $P[Q]_{j_0}$.
+On other hand, we apply same Lemma \ref{lem-Weakcompose1} on each weak open transitions $WOT_{x}$, so we obtain a new family of weak open transitions $WOT_{x}'$ in $P[Q']_{j_0}$.
+
+Suppose we have:\\[-2ex]
 \begin{mathpar}
 %\[
-\pNet\models{\openrule
-	{
-		\beta_j^{j\in J_P}\uplus(j_0\mapsto \alpha_Q), 
-		\Pred_P,  
-		\Post_Q}
-	{\ostate{S_P} \OTWeakarrow {\alpha}
-		\ostate{S'_P}}
+P\models{\openrule
+	{
+		\beta_j^{j\in J}, 
+		\Pred,  
+		\Post}
+	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
+		\ostate{(s_i')^{\, i\in L}}}
 }
@@
 	{
-		\beta_j^{j\in J_Q},
+		\set{\gamma},
 		 \Pred_Q,  
 		\Post_Q}
-	{\ostate{S_Q} \OTWeakarrow {\alpha_Q}
-		\ostate{S'_Q}}
+	{\ostate{s_{i}^{i\in L_Q}} \OTWeakarrow {\alpha_Q}
+		\ostate{(s'_{i})^{\, i\in L_Q}}}
 }%\]
@@
 
-By definition of $\mathcal{R}$ we have 
-$(s_Q,s_{Q'}, \Pred_{Q,Q'})\in\mathcal{R}_{Q,Q'}$. And thus, by definition of weak FH-bisimulation, there exist a family of weak open transitions $WOT_{x}$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j x}^{j\in J_Q}, \Pred_{Q' x},\Post_{Q' x}}
-         {\ostate{S_{Q'}}\OTWeakarrow {\alpha_{x}} \ostate{S'_{Q' x}}}
+Then, we have by lemma \ref{lem-Weakcompose}: \\[-2ex]
+	\[ P[Q]_{j_0}  
+	\models
+	{\openrule
+		{
+			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
+			\Pred\,',  \Post\,'
+			 }
+		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
+			\ostate{(s_i')^{\, i\in L\uplus L_Q}}}
+	}
+	\]
+
+On the other hand, $Q$ weak FH-bisimilar to $Q'$, so according to  Lemma  \ref{lem-alternative-weak-bisim} there exist a family of weak open transitions $WOT_{x}$:
+ \begin{mathpar}
+    \openrule
+         {
+           \gamma_{j x}^{j\in J_{x}}, \Pred_{Q_x},\Post_{Q_x}}
+         {\ostate{t_{i}^{i\in L_{Q_x}}}\OTWeakarrow {\alpha_x} \ostate{t_{ix}^{i\in L_{Q_x}}}}
 \end{mathpar}
 
-where  
-\[\forall x.\, (S'_Q,S'_{Q' x}, \Pred_{Q,Q' x})\in\mathcal{R}_{Q,Q'}\]
-and
-\begin{equation*}
-\begin{split}
-\Pred_{Q,Q'}\land \Pred_Q \implies &
-\Big(\bigvee_{x\in X}
-(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x})\Rightarrow (\Pred_{Q_x}\land\\ &~~\alpha_Q=\alpha_x \land \Pred_{Q,Q' x}\subst{\Post_{Q' x}\uplus \Post_{Q}}) \Big)
-\end{split}
-\end{equation*}
-
-Composing the OT of $P$ with the WOTs of $Q'$ by Lemma~\ref{lem-Weakcompose1} we obtain:
-\[
-\pNet[\pNetQ']_{j_0}\models\openrule
-	{
-		\vis{\beta_j^{j\in( J_P}}\uplus\gamma_{j x}^{j\in J_Q}, 
-		\Pred_P\land \Pred_{Q' x},  
-		\Post_P\uplus \Post_{Q' x}}
-	{\ostate{S_P\uplus S_{Q'}} \OTWeakarrow {\alpha}
-		\ostate{S'_P\uplus S'_{Q' x}}
+such that...\\
+
+By applying  Lemma \ref{lem-Weakcompose} on each weak open transitions $WOT_{x}$, so we obtain a new family of weak open transitions $WOT_{x}'$ in $P[Q']_{j_0}$:
+
+\[ P[Q']_{j_0}  
+	\models
+	{\openrule
+		{
+			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
+			\Pred\,',  \Post\,'
+			 }
+		{\ostate{s_i^{i\in L} \uplus t_{i}^{i\in L_{Q_x}}} \OTWeakarrow {\alpha}
+			\ostate{(s_i')^{\, i\in L} \uplus t_{ix}^{i\in L_{Q_x}} }}
 	}
 	\]
-with $\alpha_Q=\alpha_x$
-
-Side conditions necessary to prove weak-FH bisimulations are:
-
-\[\forall x.\, (S'_P\uplus S'_Q,S'_P\uplus S'_{Q' x}, \Pred_{Q,Q' x})\in\mathcal{R}\]
-which is trivially verified, and
-\begin{equation*}
-\begin{split}
-\Pred_{Q,Q'}\land \Pred_P\land \Pred_Q \implies &
-\Big(\bigvee_{x\in X}
-(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x}\land \forall j\in J_P.\, \vis{\beta_j}=\vis{\beta_j}))\Rightarrow\\
-& (\Pred_P\land \Pred_{Q' x}\land\\ &~~\alpha=\alpha \land \Pred_{Q,Q' x}\subst{\Post_P\uplus\Post_{Q' x}\uplus \Post_{Q}}) \Big)
-\end{split}
-\end{equation*}
-We conclude by observing that $\Post_P$ has no effect on variables of $Q$ and $Q'$, and thus on $\Pred_{Q,Q' x}$
-\qed
-
-% OLD
-% according to Lemma  \ref{lem-alternative-weak-bisim} for any weak open transition $WOT$ in $Q$ there exist a family of weak open transitions $WOT_{x}^{x \in X}$ in $Q'$. 
-%We apply  Lemma \ref{lem-Weakcompose1} on weak open transition $WOT$, $j_0 \in J$, we obtain a new weak open transition $WOT'$ in $P[Q]_{j_0}$.
-%On other hand, we apply same Lemma \ref{lem-Weakcompose1} on each weak open transitions $WOT_{x}$, so we obtain a new family of weak open transitions $WOT_{x}'$ in $P[Q']_{j_0}$.
-%
-%Suppose we have:\\[-2ex]
-%\begin{mathpar}
-%%\[
-%P\models{\openrule
-%	{
-%		\beta_j^{j\in J}, 
-%		\Pred,  
-%		\Post}
-%	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
-%		\ostate{(s_i')^{\, i\in L}}}
-%}
-%\quad\text{~~and~~}\quad
-%Q\models{\openrule
-%	{
-%		\set{\gamma},
-%		 \Pred_Q,  
-%		\Post_Q}
-%	{\ostate{s_{i}^{i\in L_Q}} \OTWeakarrow {\alpha_Q}
-%		\ostate{(s'_{i})^{\, i\in L_Q}}}
-%}%\]
-%
-%
-%\end{mathpar}
-%
-%Then, we have by lemma \ref{lem-Weakcompose}: \\[-2ex]
-%	\[ P[Q]_{j_0}  
-%	\models
-%	{\openrule
-%		{
-%			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
-%			\Pred\,',  \Post\,'
-%			 }
-%		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
-%			\ostate{(s_i')^{\, i\in L\uplus L_Q}}}
-%	}
-%	\]
-%
-%On the other hand, $Q$ weak FH-bisimilar to $Q'$, so according to  Lemma  \ref{lem-alternative-weak-bisim} 
-%
-%such that...\\
-%
-%By applying  Lemma \ref{lem-Weakcompose} on each weak open transitions $WOT_{x}$, so we obtain a new family of weak open transitions $WOT_{x}'$ in $P[Q']_{j_0}$:
-%
-%\[ P[Q']_{j_0}  
-%	\models
-%	{\openrule
-%		{
-%			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
-%			\Pred\,',  \Post\,'
-%			 }
-%		{\ostate{s_i^{i\in L} \uplus t_{i}^{i\in L_{Q_x}}} \OTWeakarrow {\alpha}
-%			\ostate{(s_i')^{\, i\in L} \uplus t_{ix}^{i\in L_{Q_x}} }}
-%	}
-%	\]
 
@@
 \end{theorem}
-
-\end{document}
+  \newpage
 \section{Examples of Lotos laws}

### 2019-10-16 2016-Weak-FH-Bisim/WeakBisim.tex

@@
 \end{theorem}
- \begin{proof}  (Sketch of proof) Consider $Q$ weak FH-bisimilar to $Q'$.
-It means, according to Lemma  \ref{lem-alternative-weak-bisim} for any weak open transition $WOT$ in $Q$ there exist a family of weak open transitions $WOT_{x}^{x \in X}$ in $Q'$.
-We apply  Lemma \ref{lem-Weakcompose1} on weak open transition $WOT$, $j_0 \in J$, we obtain a new weak open transition $WOT'$ in $P[Q]_{j_0}$.
-On other hand, we apply same Lemma \ref{lem-Weakcompose1} on each weak open transitions $WOT_{x}$, so we obtain a new family of weak open transitions $WOT_{x}'$ in $P[Q']_{j_0}$.
-
-Suppose we have:\\[-2ex]
+ \begin{proof}  Consider $Q$ weak FH-bisimilar to $Q'$.
+It means that there exist a FH-bisimulation $\mathcal{R}_{Q,Q'}$ relating the two pNets $Q$ and $Q'$.
+We define a relation $\mathcal{R}$ relating states of $P[Q]_{j_0}$ with states of $P[Q']_{j_0}$:
+\[\mathcal{R} = \{(\ostate{S_P\uplus S_Q},\ostate{S_P\uplus S_{Q'}}, \Pred_{Q,Q'})|\,(S_Q,S_{Q'}, \Pred_{Q,Q'})\in\mathcal{R}_{Q,Q'}\}\]
+
+To prove weak FH-bisimulation of $\pNet[\pNetQ]_{j_0}$ and 
+	$\pNet[\pNetQ']_{j_0}$, we consider  an open transition $OT$ of $\pNet[\pNetQ]_{j_0}$, and an equivalent state of $\pNet[\pNetQ']_{j_0}$, and we try to find a family of WOT of 	$\pNet[\pNetQ']_{j_0}$ that simulates $OT$.
+Consider an OT of  $\pNet[\pNetQ]_{j_0}$ it is of the form (notations introduced to prepare the decomposition):
+\[
+\pNet[\pNetQ]_{j_0}\models\openrule
+	{
+		\beta_j^{j\in( J_P\uplus J_Q)}, 
+		\Pred_P\land \Pred_Q,  
+		\Post_P\uplus \Post_Q}
+	{\ostate{S_P\uplus S_Q} \OTWeakarrow {\alpha}
+		\ostate{S'_P\uplus S'_Q}
+}
+\]
+
+By the decomposition lemma for OTs (Lemma~\ref{lem-decompose}), we obtain the 2 following OTs (equality side-conditions have been inlined for clarity):
 \begin{mathpar}
 %\[
-P\models{\openrule
-	{
-		\beta_j^{j\in J}, 
-		\Pred,  
-		\Post}
-	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
-		\ostate{(s_i')^{\, i\in L}}}
+\pNet\models{\openrule
+	{
+		\beta_j^{j\in J_P}\uplus(j_0\mapsto \alpha_Q), 
+		\Pred_P,  
+		\Post_Q}
+	{\ostate{S_P} \OTWeakarrow {\alpha}
+		\ostate{S'_P}}
 }
@@
 
-Then, we have by lemma \ref{lem-Weakcompose}: \\[-2ex]
-	\[ P[Q]_{j_0}  
-	\models
-	{\openrule
-		{
-			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
-			\Pred\,',  \Post\,'
-			 }
-		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
-			\ostate{(s_i')^{\, i\in L\uplus L_Q}}}
+By definition of $\mathcal{R}$ we have 
+$(S_Q,S_{Q'}| \Pred_{Q,Q'})\in\mathcal{R}_{Q,Q'}$. And thus, by definition of weak FH-bisimulation, there exist a family of weak open transitions $WOT_{x}$:
+ \begin{mathpar}
+    \openrule
+         {
+           \gamma_{j x}^{j\in J_Q}, \Pred_{Q' x},\Post_{Q' x}}
+         {\ostate{S_{Q'}}\OTWeakarrow {\alpha_{x}} \ostate{S'_{Q' x}}}
+\end{mathpar}
+
+where  
+\[\forall x.\, (S'_Q,S'_{Q' x}| \Pred_{Q,Q' x})\in\mathcal{R}_{Q,Q'}\]
+and
+\begin{equation*}
+\begin{split}
+\Pred_{Q,Q'}\land \Pred_Q \implies &
+\Big(\bigvee_{x\in X}
+(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x})\Rightarrow (\Pred_{Q_x}\land\\ &~~\alpha_Q=\alpha_x \land \Pred_{Q,Q' x}\subst{\Post_{Q' x}\uplus \Post_{Q}}) \Big)
+\end{split}
+\end{equation*}
+
+Composing the OT of $P$ with the WOTs of $Q'$ by Lemma~\ref{lem-Weakcompose1} we obtain:
+\[
+\pNet[\pNetQ']_{j_0}\models\openrule
+	{
+		\vis{\beta_j^{j\in( J_P}}\uplus\gamma_{j x}^{j\in J_Q}, 
+		\Pred_P\land \Pred_{Q' x},  
+		\Post_P\uplus \Post_{Q' x}}
+	{\ostate{S_P\uplus S_{Q'}} \OTWeakarrow {\alpha}
+		\ostate{S'_P\uplus S'_{Q' x}}
 }
 \]
-
-On the other hand, $Q$ weak FH-bisimilar to $Q'$, so according to  Lemma  \ref{lem-alternative-weak-bisim} there exist a family of weak open transitions $WOT_{x}$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j x}^{j\in J_{x}}, \Pred_{Q_x},\Post_{Q_x}}
-         {\ostate{t_{i}^{i\in L_{Q_x}}}\OTWeakarrow {\alpha_x} \ostate{t_{ix}^{i\in L_{Q_x}}}}
-\end{mathpar}
-
-such that...\\
-
-By applying  Lemma \ref{lem-Weakcompose} on each weak open transitions $WOT_{x}$, so we obtain a new family of weak open transitions $WOT_{x}'$ in $P[Q']_{j_0}$:
-
-\[ P[Q']_{j_0}  
-	\models
-	{\openrule
-		{
-			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
-			\Pred\,',  \Post\,'
-			 }
-		{\ostate{s_i^{i\in L} \uplus t_{i}^{i\in L_{Q_x}}} \OTWeakarrow {\alpha}
-			\ostate{(s_i')^{\, i\in L} \uplus t_{ix}^{i\in L_{Q_x}} }}
-	}
-	\]
+with $\bigvee_{x\in X}
+(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x} \implies \alpha_Q=\alpha_x$ that ensures that the open transitions can be recomposed when the OT fires.
+
+Side conditions necessary to prove weak-FH bisimulations are:
+
+\[\forall x.\, (S'_P\uplus S'_Q,S'_P\uplus S'_{Q' x}| \Pred_{Q,Q' x})\in\mathcal{R}\]
+which is trivially verified, and
+\begin{equation*}
+\begin{split}
+\Pred_{Q,Q'}\land \Pred_P\land \Pred_Q \implies &
+\Big(\bigvee_{x\in X}
+(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x}\land \forall j\in J_P.\, \vis{\beta_j}=\vis{\beta_j}))\Rightarrow\\
+& (\Pred_P\land \Pred_{Q' x}\land\\ &~~\alpha=\alpha \land \Pred_{Q,Q' x}\subst{\Post_P\uplus\Post_{Q' x}\uplus \Post_{Q}}) \Big)
+\end{split}
+\end{equation*}
+We conclude by observing that $\Post_P$ has no effect on variables of $Q$ and $Q'$, and thus on $\Pred_{Q,Q' x}$
+\qed
+
+% OLD
+% according to Lemma  \ref{lem-alternative-weak-bisim} for any weak open transition $WOT$ in $Q$ there exist a family of weak open transitions $WOT_{x}^{x \in X}$ in $Q'$. 
+%We apply  Lemma \ref{lem-Weakcompose1} on weak open transition $WOT$, $j_0 \in J$, we obtain a new weak open transition $WOT'$ in $P[Q]_{j_0}$.
+%On other hand, we apply same Lemma \ref{lem-Weakcompose1} on each weak open transitions $WOT_{x}$, so we obtain a new family of weak open transitions $WOT_{x}'$ in $P[Q']_{j_0}$.
+%
+%Suppose we have:\\[-2ex]
+%\begin{mathpar}
+%%\[
+%P\models{\openrule
+%	{
+%		\beta_j^{j\in J}, 
+%		\Pred,  
+%		\Post}
+%	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
+%		\ostate{(s_i')^{\, i\in L}}}
+%}
+%\quad\text{~~and~~}\quad
+%Q\models{\openrule
+%	{
+%		\set{\gamma},
+%		 \Pred_Q,  
+%		\Post_Q}
+%	{\ostate{s_{i}^{i\in L_Q}} \OTWeakarrow {\alpha_Q}
+%		\ostate{(s'_{i})^{\, i\in L_Q}}}
+%}%\]
+%
+%
+%\end{mathpar}
+%
+%Then, we have by lemma \ref{lem-Weakcompose}: \\[-2ex]
+%	\[ P[Q]_{j_0}  
+%	\models
+%	{\openrule
+%		{
+%			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
+%			\Pred\,',  \Post\,'
+%			 }
+%		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
+%			\ostate{(s_i')^{\, i\in L\uplus L_Q}}}
+%	}
+%	\]
+%
+%On the other hand, $Q$ weak FH-bisimilar to $Q'$, so according to  Lemma  \ref{lem-alternative-weak-bisim} 
+%
+%such that...\\
+%
+%By applying  Lemma \ref{lem-Weakcompose} on each weak open transitions $WOT_{x}$, so we obtain a new family of weak open transitions $WOT_{x}'$ in $P[Q']_{j_0}$:
+%
+%\[ P[Q']_{j_0}  
+%	\models
+%	{\openrule
+%		{
+%			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
+%			\Pred\,',  \Post\,'
+%			 }
+%		{\ostate{s_i^{i\in L} \uplus t_{i}^{i\in L_{Q_x}}} \OTWeakarrow {\alpha}
+%			\ostate{(s_i')^{\, i\in L} \uplus t_{ix}^{i\in L_{Q_x}} }}
+%	}
+%	\]
 
@@
 \end{theorem}
-  \newpage
+
+ \begin{proof}   Consider $P$ weak FH-bisimilar to $P'$.
+It means, there exist a FH-bisimulation $\mathcal{R}_{P,P'}$ relating the two pNets $P$ and $P'$.
+We define a relation $\mathcal{R}$ relating states of $P[Q]_{j_0}$ with states of $P'[Q]_{j_0}$:
+\[\mathcal{R} = \{(\ostate{S_P\uplus S_Q},\ostate{S_{P'}\uplus S_Q}, \Pred_{P,P'})|\,(S_P,S_{P'}, \Pred_{P,P'})\in\mathcal{R}_{P,P'}\}\]
+
+To prove weak FH-bisimulation of $\pNet[\pNetQ]_{j_0}$ and 
+	$\pNet'[\pNetQ]_{j_0}$, we consider  an open transition $OT$ of $\pNet[\pNetQ]_{j_0}$, and an equivalent state of $\pNet'[\pNetQ]_{j_0}$, and we try to find a family of WOT of 	$\pNet'[\pNetQ]_{j_0}$ that simulates $OT$.
+Consider an OT of  $\pNet[\pNetQ]_{j_0}$ it is of the form (notations introduced to prepare the decomposition):
+\[
+\pNet[\pNetQ]_{j_0}\models\openrule
+	{
+		\beta_j^{j\in( J_P\uplus J_Q)}, 
+		\Pred_P\land \Pred_Q,  
+		\Post_P\uplus \Post_Q}
+	{\ostate{S_P\uplus S_Q} \OTWeakarrow {\alpha}
+		\ostate{S'_P\uplus S'_Q}
+}
+\]
+
+By the decomposition lemma for OTs (Lemma~\ref{lem-decompose}), we obtain the 2 following OTs (equality side-conditions have been inlined for clarity):
+\begin{mathpar}
+%\[
+\pNet\models{\openrule
+	{
+		\beta_j^{j\in J_P}\uplus(j_0\mapsto \alpha_Q), 
+		\Pred_P,  
+		\Post_Q}
+	{\ostate{S_P} \OTWeakarrow {\alpha}
+		\ostate{S'_P}}
+}
+\quad\text{~~and~~}\quad
+Q\models{\openrule
+	{
+		\beta_j^{j\in J_Q},
+		 \Pred_Q,  
+		\Post_Q}
+	{\ostate{S_Q} \OTWeakarrow {\alpha_Q}
+		\ostate{S'_Q}}
+}%\]
+
+\end{mathpar}
+
+By definition of $\mathcal{R}$ we have 
+$(S_P,S_{P'}, \Pred_{P,P'})\in\mathcal{R}_{P,P'}$. And thus, by definition of weak FH-bisimulation, there exist a family of weak open transitions $WOT_{x}$:
+ \begin{mathpar}
+    \openrule
+         {
+           \gamma_{j x}^{j\in J_P\uplus\{j_0\}}, \Pred_{P' x},\Post_{P' x}}
+         {\ostate{S_{P'}}\OTWeakarrow {\alpha_{x}} \ostate{S'_{P' x}}}
+\end{mathpar}
+
+where  
+\[\forall x.\, (S'_P,S'_{P' x}, \Pred_{P,P' x})\in\mathcal{R}_{P,P'}\]
+and
+\begin{equation*}
+\begin{split}
+\Pred_{P,P'}\land \Pred_P \implies &
+\Big(\bigvee_{x\in X}
+(\forall j\in J_P.\, \vis{\beta_j}=\gamma_{j x} \land \vis{\alpha_Q}=\gamma_{j_0})\Rightarrow (\Pred_{Q_x}\land\\ &~~\alpha=\alpha_x \land \Pred_{P,P' x}\subst{\Post_{P' x}\uplus \Post_{P}}) \Big)
+\end{split}
+\end{equation*}
+
+We here need a special case of Lemma\ref{lem-Weakcompose}where the inner pNet $Q$ does a simple OT.
+This is just a particular case of the theorem but where notations get simplified because the inner pnet does a single transition.
+ This way we can compose the WOTs of $P'$ with the OT of $Q$ and obtain, whenever $\vis{\beta_j}=\gamma_{j x} $:
+\[
+\pNet'[\pNetQ]_{j_0}\models\openrule
+	{
+		\vis{\beta_j^{j\in( J_Q}}\uplus\gamma_{j x}^{j\in J_Q}, 
+		\Pred_{P' x}\land \Pred_Q,  
+		\Post_{P' x}\uplus \Post_Q}
+	{\ostate{S_{P'}\uplus S_{Q}} \OTWeakarrow {\alpha_x}
+		\ostate{{S'_{P' x}}\uplus S'_Q}
+}
+\]
+Side conditions necessary to prove weak-FH bisimulations are:
+
+\[\forall x.\, (S'_P\uplus S'_Q,S'_{P' x}\uplus S'_Q, \Pred_{P,P' x})\in\mathcal{R}\]
+which is trivially verified, and
+\begin{equation*}
+\begin{split}
+\Pred_{P,P'}\land \Pred_P\land \Pred_Q \implies &
+\Big(\bigvee_{x\in X}
+(\forall j\in J_P.\, \vis{\beta_j}\gamma_{j x} \land \forall j\in J_Q.\, \vis{\beta_j}=\vis{\beta_j} )\Rightarrow\\
+& (\Pred_{P' x}\land \Pred_Q\land\\ &~~\alpha_x=\alpha \land \Pred_{P,P' x}\subst{\Post_{P' x}\uplus\Post_P\uplus \Post_{Q}}) \Big)
+\end{split}
+\end{equation*}
+We conclude by observing that $\Post_Q$ has no effect on variables of $P$ and $P'$, and thus on $\Pred_{P,P' x}$
+\qed
+\end{proof}
+
+\end{document}
 \section{Examples of Lotos laws}

### 2019-10-17 2016-Weak-FH-Bisim/WeakBisim.tex
update section 3.3

--- 2019-10-16 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
-\documentclass[preprint]{elsarticle}
+\documentclass{lncs/llncs}
 
@@
 
-\newtheorem{theorem}{Theorem}
-\newtheorem{prop}{Proposition}
+%\newtheorem{theorem}{Theorem}[section]
+\newtheorem{prop}[theorem]{Proposition}
 %\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{lemma}{Lemma}
+%\newtheorem{lemma}[theorem]{Lemma}
 \newtheorem{algorithm}[theorem]{Algorithm}
 %\newtheorem{remark}[theorem]{Remark}
-\newtheorem{definition}{Definition}
-\newtheorem{property}{Property}
-\newtheorem{example}{Example}
+%\newtheorem{definition}[theorem]{Definition}
+%\newtheorem{example}[theorem]{Example}
 %\newtheorem{problem}[theorem]{Problem}
-\newenvironment{proof}{\paragraph{Proof}}{}
+%\newtheorem{proof}[theorem]{Proof}
 
@@
   between INRIA and ECNU, Shanghai}}
-\author{Ludovic Henrio  \ \ \  Eric Madelaine \ \ \ Rab\'ea}
-%\institute{Univ. of Nice Sophia Antipolis, CNRS, UMR 7271, 06900 Sophia Antipolis, France
-%	\and INRIA Sophia Antipolis M\'edit\'erann\'ee, BP 93, 06902 Sophia Antipolis, France
-%}
+\author{Ludovic Henrio\inst{1}  \ \ \  Eric Madelaine\inst{1,2} \ \ \ Rab\'ea}
+\institute{Univ. of Nice Sophia Antipolis, CNRS, UMR 7271, 06900 Sophia Antipolis, France
+	\and INRIA Sophia Antipolis M\'edit\'erann\'ee, BP 93, 06902 Sophia Antipolis, France
+}
 \date{}                                           % Activate to display a given date or no date
@@
 === en parallele
-
-\tableofcontents
 
@@
 provides the definition of pNets and introduces the notations used in
-this paper, including the definition of open pNets. 
-Section~\ref{sec:OT} defines open automata, i.e. automata
+this paper. Section~\ref{sec:OT} defines open automata, i.e. automata
 with parameters and transitions conditioned by the behaviour of
 ``holes''; a strong bisimulation equivalence for open automata is also
-presented in this section. 
-Section~\ref{section:op-semantics} gives
-the semantics of open pNets expressed as open automata, and states
+presented in this section. Section~\ref{section:op-semantics} gives
+the semantics of open pNets expressed as weak automata, and states
 compositional properties on the strong bisimulation for open
-pNets. 
-Section~\ref{sec:weak} defines a weak bisimulation
+pNets. Finally, Section~\ref{sec:weak} defines a weak bisimulation
 equivalence on open automata and derives weak bisimilarity for pNets,
 together with properties on compositionality of weak bisimulaiton for
-open pNets. 
-Finally, Section~\ref{sec:RW} discusses related works and Section~\ref{section:conclusion} concludes the
+open pNets. Finally, Section~\ref{section:conclusion} concludes the
 paper.
+
+\section{Related works}
+
+\TODO{TODO ... }
 
@@
 
-Note that for any term $t$ we have: $t\subst{\Post\shortotimes\Post'} = t\subst{\Post}\subst{\Post'}$
-
 \subsection{Parameterised Networks (pNets)}
@@
 Unfortunately, the semantics of pNets and the existing tools at this point were only able to deal with a closed system completely instantiated: pNets could be used as composition operator in the definition of the semantics, which was sufficient to perform finite-state model checking on a closed system, but there was no theory for the use of pNets as operators and no tool for proving properties on open system.
-The semantics of closed pNets~\cite{AmeurBoulifa2017}, defined as an instantiation of labelled transition systems, is not necessary to understand this article but can be useful to  understand the semantics of pNets in a simpler and more operational setting.
-The theory of pNets as operators able to fully take into account open systems is given in the following sections.
+The semmantics of closed pNets~\cite{AmeurBoulifa2017}, defined as an instantiation of labelled transition systems, is not necessary to understand this article but can be useful to  understand the semantics of pNets in a simpler and more operational setting.
+The theory of pNets as operators able to fully take into account open systems is given in the rest of this article.
 
@@
    \includegraphics[width=5.5cm]{XFIG/SimpleProt-Schema}
-   \includegraphics[width=6.5cm]{XFIG/SimpleProt-Spec}
+   \includegraphics[width=6.5cm]{XFIG/SimpleProt2-Spec}
    \caption{Specification pNet Schema and Specification}
@@
 \begin{figure}[t]
-  \centerline{\includegraphics[width=12cm]{XFIG/SimpleProt-pNet}}
+  \centerline{\includegraphics[width=12cm]{XFIG/SimpleProt2-pNet}}
   \caption{Composed pNet with the Simple Protocol Implementation}  \label{SimpleProt:Impl}
@@
 The return $ack$ message from $receiver$ to $sender$ is supposed to be safe.
+The final transmission of the message to the recipient (Hole Q) include the value of the ``error counter'' $ec$.
 
@@
 
+Fig. \ref{SimpleProt:Spec} shows the Schema of this system, and on the right side, its global specification, expressed as a pNet. 
+The full system should be equivalent (e.g. through weak bisimulation)
+to the two processes connected simply through a perfect medium. Fig. \ref{SimpleProt:Spec}, right, shows the pNet representing this global specification.
+
 Fig.
-\ref{SimpleProt:Spec} shows the Schema of this system, and on the right side, its global specification, expressed as a pNet: it should be equivalent to a simple system where the holes would be connected by a perfect reliable medium.
-
-The full system should be equivalent (e.g. through weak bisimulation)
-to the two processes connected simply through a perfect medium.
-
-\section{A model of process composition}\label{sec:OT}
-\TODO{Commenter la figure 2}
+\ref{SimpleProt:Impl} show the pNet model of the protocol.
+When the medium detects an error (modeled by a local $\tau$ action), it sends back a $m\_error$ message to the $Sender$.
+The $Sender$ increments its error counter $c$, and resend the message (including $c$) to the medium, that will, eventually, transmit $m,c$ to the receiver.
+
+\section{Open Automata: A model of process composition}
+\label{sec:OT}
 
@@
 action of some holes, the transition occurs if some predicates hold, and can involve a 
-set of state modifications. This section defines open automata and a bisimulation theory for them.
-
-\subsection{Open Automata}
+set of state modifications.
+This section defines open automata and a bisimulation theory for them.
 Open automata are not composition structures but they are made of transitions that are dependent of the actions of the holes, and they can reason on variables (potentially with only symbolic values).
@@
  FH-bisimulation is defined formally: 
- \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim} ~\\
+ \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim}
 
@@
 
-\subsection{pNet Composition Properties: composition of open transitions}
-The semantics of open pNets allows us to prove two crucial properties relating pNet composition with pNet semantics: open transition of a composed pNet can be decomposed into open transitions of its composing sub-pNets, and conversely, from the open transitions of sub-pNets,  an open transition of the composed pNet can be built.
-
-We start with decomposition: from one open transition of $P[Q]_{j_0}$, we exhibit 
-corresponding behaviours of $P$ and $Q$, and determine the relation between their 
-predicates:
-\begin{lemma}[Open transition decomposition]\label{lem-decompose} Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$}.
-	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose:
-	\[ P[Q]_{j_0}  
-		\models
-		{\openrule
-			{
-				\beta_j^{j\in J}, \Pred,  
-				\Post}
-			{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
-				\ostate{s_i'^{\, i\in L}}}
-		}
-	\]
-		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.
-		 Then there exist $\alpha_Q$, $\Pred\,'$, $\Pred\,''$, 
-		$\Post\,'$, $\Post\,''$ s.t.:\\[-2ex]
-		%\[
-		\begin{mathpar}
-		P\models{\openrule
-			{
-				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
-				\Pred\,',  
-				\Post\,'}
-			{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {\alpha}
-				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
-		}%\]
-	\vspace{-2.2ex}\\\text{and~~}
-		%\[
-		Q\models{\openrule
-			{
-				\beta_j^{j\in J\cap\Holes(Q)}, \Pred\,'',  
-				\Post\,''}
-			{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
-				\ostate{s_i'^{\,i\in L_Q}}}
-		}%\]
-		\end{mathpar}
-		and  $\Pred \iff \Pred\,'
-		\land \Pred\,''\land \alpha_Q=\beta_{j_0}$, $\Post=\Post\,'\uplus 
-		\Post\,''$ where $\Post\,''$ is the restriction of $\Post$ over variables of 
-		$\Leaves(Q)$.
-\end{lemma}
-
-Lemma \ref{lem-compose} is combining an open transition of $P$ with
-an open transition of $Q$, and building a corresponding transition of
-$P[Q]_{j_0}$, assembling their predicates.
-\paragraph{Lemma~\ref{lem-compose}} {\bf Open transition composition}\\
-	Suppose $j_0\in J$ and:\\[-2ex]
-\begin{mathpar}
-%\[
-P\models{\openrule
-	{
-		\beta_j^{j\in J}, 
-		\Pred,  
-		\Post}
-	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
-		\ostate{s_i'^{\, i\in L}}}
-}%\]
-\text{~~and~~}
-%\[
-Q\models{\openrule
-	{
-		\beta_j^{j\in J_Q},
-		 \Pred\,',  
-		\Post\,'}
-	{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
-		\ostate{s_i'^{\, i\in L_Q}}}
-}%\]
-\end{mathpar}
-Then, we have\\[-2ex]
-	\[ P[Q]_{j_0}  
-	\models
-	{\openrule
-		{
-			\beta_j^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
-			\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0},  
-			\Post\uplus \Post\,'}
-		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {\alpha}
-			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
-	}
-	\]
-
-Note that this does not mean that any two pNets can be composed and produce an open 
-transition. Indeed, the predicate $\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0}$ is often not  satisfiable, for example if the action  $\alpha_Q$ cannot be matched with $\beta_{j_0}$.
-Note also that $\beta_{j_0}$ is  only used as an intermediate term inside formulas in the composed open transition: it 
-does not appear neither as global action nor as an action of a hole.
-
-\subsection{Bisimulation for open pNets -- a Composable Bisimulation Theory}
+\subsection{Bisimulation for open pNets and Composability}
 \label{section:bisimulation-PN}
@@
 synchronisation with their context.
-The notions of non-observable action varies in different contexts,
-e.g. $tau$ in CCS, and $i$ in Lotos, we could define classically a set of
-\emph{internal/non-observable actions} depending on a specific action
-algebra. In this paper, to simplify the notations, we will simply use $\tau$ as the single non-observable action; the generalisation of our results to a set of non-observable actions is trivial. 
-Naturally, a non-observable action cannot be synchronised with
+As the notions of invisible action varies in different contexts,
+e.g. $tau$ in CCS, and $i$ in Lotos, we will rely here on some set of
+\emph{internal actions} depending on a specific action
+algebra. Naturally, an internal action cannot be synchronised with
 actions of other systems in its environment.
-We show here that under such assumption of non-observability of $\tau$ actions, see Definition~\ref{def:Non-ObsTau}, we can define a weak bisimulation relation that is compositional, in the sense of open pNet composition.
-In this section we will first define a notion of weak open transition similar to open transition.
-In fact a weak open transition is made of several open transitions labelled as non-observable transitions, plus potentially one observable open transition.
+We show here that under such assumption of non-observability of internal actions, we can define a weak bisimulation relation that is compositional, in the sense of open pNet composition.
+In this section we will first define a notion of weak transition similar to open transition.
+In fact a weak open transition is made of several open transitions labelled as internal transitions, plus potentially one non-internal open transition.
 This allows us to define weak open automata, and a weak bisimulation relation based on these weak open automata.
@@
 
-\subsection{Preliminary definitions and notations}
-
-We first specify in terms of open transition, what it means for an action to be non-observable.
-Namely, we constraint ourselves to system where the emission of a $\tau$ action by a sub-pNet cannot be observed by the surrounding pNets.
-In other words, a pNet cannot change its state, or emit a specific observable action when one of its holes emits a $\tau$ action.
-
-More precisely, we state that $\tau$ is not observable if the automaton always allows any $\tau$ transition from holes, and additionally the global transition resulting from a $\tau$ action of a hole is a $\tau$ transition not changing the pNet's state.
+\subsection{Defining weak open transitions}
+
+Intuition: tau is non observable if the automaton allows any tau transition from holes, and the global transition resulting from a tau in a hole is a tau transition not changing the action state.
 We define $\Id(s)$ as the identity function on variables of state s.
-\begin{definition}[Non-observability of $\tau$ actions]\label{def:Non-ObsTau}
-An open automaton $A = <J,\mathcal{S},s_0,\mathcal{T}>$ \emph{cannot observe $\tau$ actions} if and only if for all $j$ in $J$ and $s$ in $\mathcal{S}$ we have:
+\begin{definition}[Non-observability of silent actions]\label{def:Non-ObsTau}
+An open automaton $A = <J,\mathcal{S},s_0,\mathcal{T}>$ \emph{cannot observe silent actions} if and only if for all $j$ in $J$ and $s$ in $\mathcal{S}$ we have
 \begin{enumerate}
@@
 and 
-\item for all $\beta_j$, $J$,  $\alpha$,  $s$, $s'$, $\Pred$, $\Post$  such that
+\item for all $A$, $\alpha$,  $s$, $\Post$ and $s'$ such that
 \[ \openrule
@@
          {s \OTarrow {\alpha} s'}
-         \in \mathcal{T} \] If there exists $j$ such that $\beta_j=\tau$ then we have: \[ \alpha=\tau\land s=s'\land \Pred=\True\land\Post=\Id(s) \land J=\{j\}
+         \in \mathcal{T} \] If there is a $j$ such that $\beta_j=\tau$ then we have \[ \alpha=\tau\land s=s'\land \Pred=\True\land\Post=\Id(s) \land J=\{j\})
 \]
@@
 \end{definition}
-The first statement of the definition states that the open automaton must allow a hole to do a silent action at any time, and must not observe it, i.e.
+The first statement of the definition state that the open automaton must allow a hole to do a silent action at any time, and must not observe it, i.e.
 cannot change its internal state because a hole did a $\tau$ transition.
-The second statement ensures that there cannot be in the open automaton other transitions that would be able to observe a $\tau$ action from a hole.
-The condition $J=\{j\}$ is a bit restrictive, it could safely be replaced by $\forall j\in J.\, \beta_j=\tau$, allowing the other holes to perform $\tau$ transitions too (because these $\tau$ actions cannot be observed).
-
-By definition, one weak open transition contains  several open transitions, where  each open transition can require an observable action from a given hole, the same hole might have to emit several observable actions for a single weak open transition to occur.
-Consequently, for a weak open transition to trigger, a list of actions from a given hole might be required.
-
-Thus, we let $\gamma$ range over lists of action terms and use $\dotcup$ as the union operator that appends lists of action terms: given two  lists of action terms  $\gamma\dotcup\gamma '$ concatenates the two lists.
-The operation is lifted to indexed sets of lists:  $\set {\gamma_1}\dotcup \set {\gamma_2}$ is an indexed set of lists such that, at each index $i$, $\set {\gamma_1}\dotcup \set {\gamma_2}$ concatenates the list of  actions at index $i$ of $\set{\gamma_1}$ and the one at index $i$ of $\set {\gamma_2}$\footnote{One of the two lists is empty when $i\not \in \dom(\set{\gamma_1})$ or $i\not \in \dom(\set{\gamma_2})$ .}.
-$[a]$ denotes a list with a single element.
-
-As required actions are now sequences of observable actions, we need an operator to build them from set of actions that occur in open transitions.
-Thus we define $\vis{\set\beta}$ as the mapping $\set\beta$  with only observable actions but where each element is either empty or a list of length 1:
- \[\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}\text{ where }I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}\]
-
-\subsection{Weak open transition definition}
-
-Because of the non-observability property (Definition~\ref{def:Non-ObsTau}), it is possible to add any number of $\tau$ transitions of the holes before or after any open transition freely.
+The second statement ensures that there cannot be in the open automaton other transitions that would be able to observe a silent action from a hole.
+The condition $J=\{j\}$ is a bit restrictive, it could safely be replaced by $\forall j\in J.\, \beta_j=\tau$, allowing the other holes to perform silent transitions too (because these silent actions cannot be observed).
+
+We then can add any number of $\tau$ transitions of the holes before or after any open transition freely.
 This property justifies the fact that we can abstract away $\tau$ transitions from holes in the definition of a weak open transition.
 
-%
-%Classically, we start by defining a derived transition relation based
-%on sequences of invisible actions.
+Classically, we start by defining a derived transition relation based
+on sequences of invisible actions:
 
 \def\InvAct{\mathcal{Inv}}
-%
-%\RAB{We let $\gamma$ range over words (of action terms) and use $\dotcup$ as the union that appends words.}
+
+\RAB{We let $\gamma$ range over words (of action terms) and use $\dotcup$ as the union that appends words.}
+
+We let $\gamma$ range over lists of action terms and use $\dotcup$ as the union that appends lists of action terms: given two  lists of action terms  $\gamma\dotcup\gamma '$ concatenates teh two lists.
+The operation is lifted to indexed sets of lists where  $\set {\gamma_1}\dotcup \set {\gamma_2}$ is an indexed set of lists that at each index concatenates the listof  list of $\set{\gamma_1}$ and the one of $\set {\gamma_2}$ (where one of the two lists is empty when $j\not \in \dom(\set{\gamma_1})$).
+$[a]$ is a list with a single element.
 
@@
 
-A weak open transition labelled $\alpha$ can be seen as a sequence of open transitions that are all labelled $\tau$ except one that is labelled $\alpha$; however conditions on predicates, effects, and states must be verified for this sequence to be enactable.
-
-We are now able to build a weak open automaton from an open automaton.
-This is done in a way that resembles the process of $\tau$ saturation: we add  $\tau$ open transitions before or after another (observable or not) open transition.
+We can rewrite a weak open transition  $ \OTWeakarrow {\alpha}$ as a sequence of open transitions $(\OTarrow{\tau})^* (\OTarrow{\alpha})(\OTarrow{\tau})^* $.
+
+We define $\vis{\set\beta}$ as the mapping $\set\beta$  without  invisible actions but where each element is now a list (if length 1).\\ $\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}$ s.t.
+$I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}$.
+
 \begin{definition}[Building a weak open automaton]\label{def:buildweakOT}
@@
 The weak open automaton \emph{derived} from $A$ is an open automaton  $<J,\mathcal{S},s_0,\WT>$ where $\WT$ is derived from $\mathcal{T}$ as follows:
+
 %\noindent{\bf Invisible $\tau$ transitions:}
@@
 \end{definition}
-Rule $\WTUn$ states that it is always possible to do a null $\tau$ transition, where the state is unchanged and the holes perform no action.
-Rule~$\WTDeux$ states that each open transition can be considered as a weak open transition.
-The last rule is the most interesting:  Rule~$\WTTrois$ allows any number of $\tau$ transitions before or after a weak open transition.
-This rules carefully composes predicates, effects, and actions of the holes, indeed in the rule, predicate $\Pred_2$ manipulates variables of $s_1$ that result from the first weak open transition.
-Their value thus depend of the initial state but also of the effect (as a substitution $\Post_1$) of the first weak open transition.
-In the same manner, $\Pred_3$ must be applied the joint substitution $\Post_2\bigotimes\Post_1$.
-Similarly, effects on variables must be applied to obtain the global effect of the composed weak open transition, it must also be applied to observable actions of the holes, and to the global action of the weak open transition	.
 
 \TODO{Eric: try to draw (ATG) the weak transitino versions of the Simple Protocol, both Spec (easy) and Impl (check readability?)}
-
-\subsection{Composition properties: composition of weak open transitions}
-Now the semantics of an open pNet is defined both as an open automaton, and as a weak open automaton.
-Like the open automaton, the weak open automaton features valuable composition properties.
-We can exhibit  a composition property and a decomposition property that relate open pNet composition with their semantics, defined as weak open automata.
-These are technically more complex than the ones for open automata because each hole performs a set of actions, and thus a composed transition is the composition of one transition of the top-level pNet and a sequence of transitions of the sub-pnet that fills its hole.
 
@@
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
-   \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
+   \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \Rightarrow\! \Pred_{OT_x}
      \!\land\! \alpha\!=\!\alpha_x\! \land\!  
@@
 
-\subsection{Properties of weak bisimulation for open pNets}
-
 \begin{theorem}[Congruence for  weak bisimulation]\label{weak-thm-congr-eq}
@@
 pick all $\tau^*$ and $\tau^*;a;\tau^*$ sequences from the OA, and build a weak
-open trnsition from each sequence. Here is one example of a short sequence,
+OT from each sequence. Here is one example of a short sequence,
 starting with the open transition $OT_2$ of page \pageref{OT:ABP},
@@
 receiver control bits are equal), and to the environment. The two
-firsts open transitionTs are internal, the last one is visible, so it constitute a
+firts OTs are internal, the last one is visible, so it constitute a
 $\tau;\tau;a$ weak transition.
@@
 
-\section{Related Works}\label{sec:RW}
+\section{Related Works}
 
@@
        	\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}
-       	\left( \forall j. \beta_j=\beta_{jpx}  \land \Pred_{OT_{px}}
+       	\left( \forall j. \beta_j=\beta_{jpx}  \Rightarrow \Pred_{OT_{px}}
        	\land \alpha\!=\!\alpha_{px} \land
@@
        	\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}\!
-       	\left( \forall j.\beta_{jpx}\!=\!\beta_{jpxy} \land\! \Pred_{OT_{pxy}}\!
+       	\left( \forall j.\beta_{jpx}\!=\!\beta_{jpxy} \Rightarrow\! \Pred_{OT_{pxy}}\!
        	\land\! \alpha_{px}\!=\!\alpha_{pxy} \!\land\!
@@
        		P, x\in X, 
-       		y\in Y} \subseteq \mathcal{T}_3$ that should simulate $OT$.
+       		y\in Y} \subseteq \mathcal{T}_3$ that should simulate \emph{OT}.
 
@@
        		\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
-       		\left( \forall j. \beta_j=\beta_{jpxy}  \land \Pred_{OT_{pxy}}
+       		\left( \forall j. \beta_j=\beta_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
        		\land \alpha\!=\!\alpha_{pxy} \land
@@
        		\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}
-       		\left( \forall j. \beta_j=\beta_{jpx}  \land \Pred_{OT_{px}}
+       		\left( \forall j. \beta_j=\beta_{jpx}  \Rightarrow \Pred_{OT_{px}}
        		\land \alpha\!=\!\alpha_{px} \land
@@
        		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-       		\left( \forall j. \beta_j=\beta_{jpx}  \land 
+       		\left( \forall j. \beta_j=\beta_{jpx}  \Rightarrow 
        		(\Pred_{OT_{px}}\land\Pred_{p,u})
@@
        		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-       		\big( \forall j. \beta_j=\beta_{jpx}  \land (\bigvee_{y\in Y} 
-       		\big( \forall j'. \beta_{j'px}=\beta_{j'pxy}  \land \Pred_{OT_{pxy}}
+       		\big( \forall j. \beta_j=\beta_{jpx}  \Rightarrow (\bigvee_{y\in Y} 
+       		\big( \forall j'. \beta_{j'px}=\beta_{j'pxy}  \Rightarrow \Pred_{OT_{pxy}}
        		\land \alpha_{px}\!=\!\alpha_{pxy}\\~\hspace{3em}~ \land
@@
        		\big( \forall j, j'. \beta_j=\beta_{jpx} \land \beta_{j'px}=\beta_{j'pxy}
-       		\land \big( 
+       		\Rightarrow \big( 
        		\Pred_{OT_{pxy}}
@@
 \big( \forall j, j'.\beta_j=\beta_{jpx} \land \beta_{j'px}=\beta_{j'pxy}
-\land\\ ~\hspace{7em} 
+\Rightarrow\\ ~\hspace{7em} 
 \Pred_{OT_{pxy}}
@@
 \hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
-\left( \forall j. \beta_j\!=\!\beta_{jpxy}  \land \Pred_{OT_{pxy}}
+\left( \forall j. \beta_j\!=\!\beta_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
 \land \alpha\!=\!\alpha_{pxy} \land
@@
 between the context and the internal pNet, and with their recomposition. 
-
-\paragraph{Lemma~\ref{lem-decompose}}: {\bf Open transition decomposition} \\
- Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$}.
+We start with decomposition: from one open transition of $P[Q]_{j_0}$, we exhibit 
+corresponding behaviours of $P$ and $Q$, and determine the relation between their 
+predicates:
+
+\begin{lemma}[OT decomposition]\label{lem-decompose} Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$}.
 	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose:
@@
 		$\Leaves(Q)$.
+\end{lemma}
 
@@
 
-Now focus on OTs\footnote{In the appendix we use OT to abbreviate ``open transition'' and WOT to stand for ``weak open transition.''} of the subnets.
-For each $m\in I_1\uplus I_2$ we have one of the two
+Now focus on OTs of the subnets. For each $m\in I_1\uplus I_2$ we have one of the two 
 following OT\footnotemark[\thefootnote]:\\
@@
 
+Lemma \ref{lem-compose} is combining an open transition of $P$ with
+an open transition of $Q$, and building a corresponding transition of
+$P[Q]_{j_0}$, assembling their predicates.
+
 \begin{lemma}[Open transition composition]\label{lem-compose} 
@@
 \end{lemma}
-
+\TODO{important comment added:}
 Note that this does not mean that any two pNets can be composed and produce an open 
@@
  \Rightarrow \displaystyle{\bigvee_{x\in X}
- \left( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \land 
+ \left( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \Rightarrow 
  \Pred_{OT_x}
@@
  	{\displaystyle\bigvee_{x\in X}
- 	\left( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \land 
+ 	\left( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \Rightarrow 
  	\Pred_{OT_x}
@@
  	{\displaystyle\bigvee_{x\in X}
- 		\left( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \land 
+ 		\left( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \Rightarrow 
  		\Pred\,'\land \Pred_{OT_x}
@@
 \[{\displaystyle\bigvee_{x\in X}
- 		\left( \forall j\in J. \beta_j=\beta_{jx}  \land 
+ 		\left( \forall j\in J. \beta_j=\beta_{jx}  \Rightarrow 
  		\left(\Pred\,'\land \Pred_{OT_x}
@@
 		 \Rightarrow \bigvee_{x\in X}
-			\left( \forall j\in J'. \beta_j=\beta_{jx}  \land 
+			\left( \forall j\in J'. \beta_j=\beta_{jx}  \Rightarrow 
 			\Pred_{OT_x}
@@
 {\displaystyle{\bigvee_{x\in X}\!(\forall j\!\in\! J'. \beta_j\!=\!\beta_{jx}  
-\land \!
+\Rightarrow \!
 \Pred_{OT_x}\land \alpha_Q=\beta_{j_0}
@@
 	{\displaystyle{\bigvee_{x\in X}\!(\forall j\!\in\! J'. \beta_j\!=\!\beta_{jx}  
-\land \!
+\Rightarrow \!
 \left(\Pred_{OT_x}\land
@@
 
-We  define a quantified composition operator for effects, i.e.$\Post$ elements of the open transitions.
-We use ${\displaystyle \bigotimes_{i=n}^{0} \Post_i}$ to denote  $\Post_n\otimes .. \otimes \Post_0$. By convention ${\displaystyle \bigotimes_{i=-1}^{0} \Post_i}$ is the identity.
-
+We use ${\displaystyle \bigotimes_{i=n}^{0} \Post_i}$ to denote  $\Post_n\otimes ..
+\otimes \Post_0$.
+By convention ${\displaystyle \bigotimes_{i=-1}^{0} \Post_i}$ is the identity.
+Note that for any term $t$ we have: $t\subst{\Post\shortotimes\Post'} = t\subst{\Post}\subst{\Post'}$
+
+\TODO{attention a l ordre: inverse d avant mais colle mieux a la notation -- check everywhere below}
 \subsection{Weak bisimulation is an equivalence}
-
-In this section, we first define two alternative definitions for weak bisimulation.
-We use these two alternative definitions to show that weak bisimulation is an equivalence, we will also re-use these alternative definitions in the  proofs of the theorems in next sections.
 
@@
 
- and similarly for $\Pred_{4i}$, $\Pred_{5i}$, $\Post_{4i}$, and $\Post_{5i}$.
-
-Also, we have the following assertions:\\
+ and similarly for $\Pred_{4i}$, $\Pred_{5i}$, $\Post_{4i}$, and $\Post_{5i}$  \TODO{define or OK this way?}
+
+We have the following assertions:\\
 $
@@
 \displaystyle{\implies\!\!\! \bigvee_{x\in X}
-   \left( \forall j\in J_x.\gamma_j=\gamma_{jx}  \land \Pred_{OT_x}
+   \left( \forall j\in J_x.\gamma_j=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
      \land \alpha\!=\!\alpha_x \land  
@@
            \gamma_{j a}^{j\in J_{a}}, \Pred_{OT_a},\Post_{OT_a}}
-         {t \OTWeakarrow {\alpha_{1 a}} u_a}
+         {u \OTWeakarrow {\alpha_{1 a}} u_a}
 \end{mathpar}
- such that  $\forall a, J_{a}=\{j\in J_1'|\beta_{1j}\neq\tau\},   (s_{11},u_a|\Pred_{s_{11},u_a})\in \mathcal{R}$ and \\
+ such that  $\forall a, J_{a}=\{j\in J_1'|\beta_{1j}\neq\tau\}, u=t,  (s_{11},u_a|\Pred_{s_{11},u_a})\in \mathcal{R}$ and \\
  $\Pred_{s,t} \land \Pred_1\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
-  \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}=\gamma_{ja}  \land \Pred_{OT_a}
+  \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a}
      \land \alpha_{1 a}\!=\!\tau \land  
@@
            \gamma_{j a}^{j\in J_{a}}, \Pred_{OT_a},\Post_{OT_a}}
-         {t \OTWeakarrow {\tau} u_a}
+         {u \OTWeakarrow {\tau} u_a}
 \end{mathpar}
@@
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{b\in B}}
- \!\!  \left( \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}\land \Pred_{OT_{b}}\!\land \alpha'\!=\!\alpha_{2 b} \land  
+ \!\!  \left( \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}\Rightarrow \Pred_{OT_{b}}\!\land \alpha'\!=\!\alpha_{2 b} \land  
      \Pred_{s_{21},v_{b}}\subst{\Post_2\uplus\Post_{OT_{b}}}\right)$
@@
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{c\in C}}
-   \!\left( \forall j\in J_{c}. \vis{\beta_{3j}}\!=\!\gamma_{jc} \! \land\! \Pred_{OT_{c}}\!
+   \!\left( \forall j\in J_{c}. \vis{\beta_{3j}}\!=\!\gamma_{jc} \! \Rightarrow\! \Pred_{OT_{c}}\!
      \land\!  
@@
 		\Pred, \Post}  
-         {t \OTWeakarrow {\alpha''} w_{c}} 
+         {u \OTWeakarrow {\alpha''} w_{c}} 
 } 
@@
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} 
-  ( \forall j\in J. \gamma_j'=\gamma_{j}  \land \Pred
+  ( \forall j\in J. \gamma_j'=\gamma_{j}  \Rightarrow \Pred
      \land \alpha \!=\! \alpha'' \land  
      \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,})$\\
-We have:\\
+     Let's start with the hypothesis \TODO{ je vois pas ce que u=t apporte -- Ludo} and consider  $u=t$   we have:\\
 $\Pred_{OT}= \Pred_1 \wedge \Pred_2\subst{\Post_1} \wedge \Pred_3\subst{\Post_2\shortotimes\Post_1}$\\
@@
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
- \! \! \left( \forall j\in J_a. \vis{\beta_{1j}}=\gamma_{ja}  \land \Pred_{OT_a}
+ \! \! \left( \forall j\in J_a. \vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a}
       \land  
@@
  \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
-  \!\! ( \forall j\in J_a. \vis{\beta_{1j}}=\gamma_{ja}  \land \Pred_{OT_a} \land
+  \!\! ( \forall j\in J_a. \vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a} \land
      \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}) \wedge\\ \Pred_2\subst{\Post_1\uplus\Post_{OT_a}}  \\
@@
  \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
-\!\!   \left(\forall j\in J_a. \vis{\beta_{1j}}\!=\!\gamma_{ja}\land \Pred_{OT_a}
+\!\!   \left(\forall j\in J_a. \vis{\beta_{1j}}\!=\!\gamma_{ja}\Rightarrow \Pred_{OT_a}
      \!\land(\Pred_{s_{11},u_a}\wedge\Pred_2)\subst{\Post_1\uplus\Post_{OT_a}} \right)$\\
@@
  \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
-   \!\!(\forall j\in J_a. \vis{\beta_{1j}}\!\!=\!\gamma_{ja}  \land \Pred_{OT_a}
+   \!\!(\forall j\in J_a. \vis{\beta_{1j}}\!\!=\!\gamma_{ja}  \Rightarrow \Pred_{OT_a}
       \land (\displaystyle{\bigvee_{b\in B}}(
     \forall j\in J_{b}.
-\vis{\beta_{2j}}\!=\!\gamma_{jb}  \land \Pred_{OT_{b}}\land \\~\qquad\qquad\alpha'\!=\!\alpha_{2 b}\!
+\vis{\beta_{2j}}\!=\!\gamma_{jb}  \Rightarrow \Pred_{OT_{b}}\land \alpha'\!=\!\alpha_{2 b}\!
 \land \Pred_{s_{21},v_{b}}\subst{\Post_2\uplus\Post_{OT_{b}}})\subst{\Post_1\uplus\Post_{OT_a}})$\\
@@
 \vis{\beta_{1j}}\!\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-(\vis{\beta_{2j}}\!=\!\gamma_{jb})\subst{\Post_1\uplus\Post_{OT_a}}   \land\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_1\uplus\Post_{OT_a}} \land  (\alpha'\!=\!\alpha_{2 b}) \subst{\Post_1\uplus\Post_{OT_a}} \land \\ \Pred_{s_{21},v_{b}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
+(\vis{\beta_{2j}}\!=\!\gamma_{jb})\subst{\Post_1\uplus\Post_{OT_a}}   \Rightarrow\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_1\uplus\Post_{OT_a}} \land  (\alpha'\!=\!\alpha_{2 b}) \subst{\Post_1\uplus\Post_{OT_a}} \land \\ \Pred_{s_{21},v_{b}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
 Since $Post_1$  does not act on $\gamma_{jb}$, nor on $ \Pred_{OT_{b}}$ and $  \alpha_{2}$.
@@
 \vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-\vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jb} \subst{\Post_{OT_a}}  \land\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_{OT_a}} \land \alpha'\subst{\Post_1}=\alpha_{2 b} \subst{\Post_{OT_a}} \land \Pred_{s_{21},v_b}\\\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
+\vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jb} \subst{\Post_{OT_a}}  \Rightarrow\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_{OT_a}} \land \alpha'\subst{\Post_1}=\alpha_{2 b} \subst{\Post_{OT_a}} \land \Pred_{s_{21},v_b}\\\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
 Finally, the conjunction with the term $\Pred_3\subst{\Post_2\shortotimes\Post_1}$ of the both sides of the implication and rewriting, we get:\\
@@
 (\forall j\in J_a.\vis{\beta^1_j}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-\vis{\beta_{2j}}\subst{\Post_1}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}\land \Pred_{OT_a}\land\Pred_{OT_{b}}\subst{\Post_{OT_a}} \land  \alpha'\subst{\Post_1}= \alpha_{2 b} \subst{\Post_{OT_a}} \land (\Pred_{s_{21},v_b} \land  \Pred_3)\\ \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{b}}\shortotimes\Post_{OT_a}})$\\
+\vis{\beta_{2j}}\subst{\Post_1}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}\Rightarrow \Pred_{OT_a}\land\Pred_{OT_{b}}\subst{\Post_{OT_a}} \land  \alpha'\subst{\Post_1}= \alpha_{2 b} \subst{\Post_{OT_a}} \land (\Pred_{s_{21},v_b} \land  \Pred_3)\\ \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{b}}\shortotimes\Post_{OT_a}})$\\
 Again note that because of the domain  of the substitution is independent from some predicates and expressions, we removed $\Post_1$ and  we  added the term $\Post_{OT_{b}}\shortotimes\,\Post_{OT_a}$ in the substitution of the right side of the implication.\\
@@
 (\forall\! j\in\! J_a.\vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \!\in\! J_{b}.\vis{\beta_{2j}\subst{\Post_{OT_a}}}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}  \land 
- \forall j\!\in\! J_{c}. \vis{\beta_{3j} \subst{\Post_2\,\shortotimes\,\Post_1}} \!=\!\gamma_{jc} \subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}  \land\\
+ \forall j\!\in\! J_{c}. \vis{\beta_{3j} \subst{\Post_2\,\shortotimes\,\Post_1}} \!=\!\gamma_{jc} \subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}  \Rightarrow\\
    \underbrace{\Pred_{OT_a}\land\Pred_{OT_{b}} \subst{\Post_{OT_a}} \land 
@@
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}} \displaystyle{\bigvee_{b\in B}} \displaystyle{\bigvee_{c\in C}} 
-(\forall j\in J.\gamma_j'=\gamma_j \land  \Pred \land \alpha=\alpha''  \land \Pred_{s',w_{c}}\subst{\Post_{OT}\uplus\Post\,}$\\
+(\forall j\in J.\gamma_j'=\gamma_j \Rightarrow  \Pred \land \alpha=\alpha''  \land \Pred_{s',w_{c}}\subst{\Post_{OT}\uplus\Post\,}$\\
 
@@
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} 
-(\forall j\in J.\gamma_j'=\gamma_j \land  \Pred \land \alpha=\alpha''  \land \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,}$\\
+(\forall j\in J.\gamma_j'=\gamma_j \Rightarrow  \Pred \land \alpha=\alpha''  \land \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,}$\\
 \qed
@@
 
-\TODO{attention theorem 10 est le thm 6 en fait -- presentation des thm et preuve a revoir}
 \begin{theorem}[Weak FH-Bisimulation is an equivalence]\label{thm-weak-equiv} Suppose $\mathcal{R}$ 
@@
 \subsection{Composition properties}
-This section gives detailed lemmas and their proofs, these are the equivalent of the composition lemmas for open transitions, but applied to weak automata that give the semantics of open pNets.
-
-\begin{lemma}[Weak open transition decomposition]\label{lem-decomposeWOT} 
+
+\begin{lemma}[Weak OT decomposition]\label{lem-decomposeWOT} 
 	Let $\Leaves(Q)=pLTS_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
@@
 				}%\]
-,$  \\
+,$
 $ Q\models{\openrule
@@
 $
-and \\
+and
 $\forall p \in [0..n_2] Q\models{\openrule
@@
 \end{equation*}
-We can obtain similar equations for $\alpha_{n_1+1}$ related with $\beta_{2 j_0}$ and the  $\alpha_k$ for $k\geq n_1+2$ related with $\beta_{3 p j_0}$ for some $p$.
+We can optain similar equations for $\alpha_{n_1+1}$ related with $\beta_{2 j_0}$ and the  $\alpha_k$ for $k\geq n_1+2$ related with $\beta_{3 p j_0}$ for some $p$.
 Note that the substitutions are however more complex.
-Overall we obtain (we skip here the details about the three cases 1, 2, and 3 above that all fall into the same equation because of the re-indexing we perform): 
-\begin{equation}\label{eqproofbeta}
-\Pred_\beta \iff \gamma_{j_0}=
-\vis{[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post''_{j}}|p\in[0..n_1+n_2+2]]}
-\end{equation}
+\TODO{detailler les equations?}
+
+Overall we obtain (we skip here the details about the three cases 1, 2, and 3 above that all fall into the same equation because of the re-indexing we perform) \[\Pred_\beta \iff \gamma_{j_0}=
+\vis{[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post''_{j}}|p\in[0..n_1+n_2+2]]}\]
 
@@
 
-Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (they are $\tau$ transitions).
-By considering the sequence of $\tau$ and non-$\tau$ actions we split the sequence of actions into $n+1$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.
-
-\begin{figure}
-\begin{center}
+Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (are $\tau$ transition).
+By considering $\tau$  actions we split the sequence of actions into $n+1$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.
+We can decompose each of the $n+1$ subsequences;
+
 \includegraphics[width=6cm]{XFIG/proof-explain}
-\end{center}\caption{Composition of the subsequences}\label{figproof}
-\end{figure}
-
- We can decompose each of the $n+1$ subsequences in the following way (see Figure~\ref{figproof}).
-For $k\in [0..n]$ the position of the $k^{\text{th}}$ visible action is  $n_k$.
-For $l\in [1..n]$,  $n'_l$ is any index between $n_{l-1}$ and $n_l$, additionally $n'_0=0$ and $n'_{n+1}=n_1+n_2+3$.
+
+for $k\in [0..n]$ the position of the $k^{\text{th}}$ visible action is  $n_k$, for $k\in [1..n]$,  $n'_k$ is any index between $n_{k-1}$ and $n_k$, additionally $n'_0=0$ and $n'_{n+1}=n_1+n_2+3$.
 We obtain $n+1$ subsequences  made of the following OTs, for all $k\in [0..n]$ :\\
@@
 				}%\]
-,$ \\
+,$ 
 $Q\models{\openrule
@@
 $
-and\\
+and
 $\forall p \in [(n_k\!+\!1)..(n'_{k+1}\!-\!1)]\,\, Q\models{\openrule
@@
 \alpha_k'\displaystyle{\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}}\]
-With~\ref{eqproofbeta}, we now have (the actions $\alpha'_p$ correspond to the observable actions, $\alpha_k$): 
+We now have (the $\alpha'_p$ correspond to the observable $\alpha_k$ actions): \TODO{add ref to eq 1 page above?}
 \begin{eqnarray*}
@@
 
-Indeed,
+Indeed, \TODO{fill the empty lines (more complex but easy adaptation)}
 {\scriptsize \begin{equation*}
@@
 \end{multline*}
-Now, when $j\in J_t$ for some $t$,  $\gamma'_j$ is the concatenation of elements of $\gamma'_{1ij}$, $\gamma'_{2 j}$, $\gamma'_{3ij}$  that are not empty.
+Now, when $j\in J_t$ for some $t$,  $\gamma'_j$ is the concatenation of elements of $\gamma'_{1ij}$, $\gamma_2'$, $\gamma'_{3ij}$  that are not empty.
 By construction the concatenation of these elements is $\gamma_{tj}$, for $t\in[0..n]$.
@@
 \gamma'_j&=
-\mybigdotcup_{i=0}^{m_1}{\gamma'_{1ij}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{1k}}\dotcup
- {\gamma'_{2 j}}\subst{\bigotimes_{k=m_1}^{0}\Post\,'_{1k}}\dotcup
- \mybigdotcup_{i=0}^{m_2}{\gamma'_{3ij}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}\\
+\mybigdotcup_{i=0}^{m_1}\set{\gamma'_{1i}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{1k}}\dotcup
+ \set{\gamma'_{2}}\subst{\bigotimes_{k=m_1}^{0}\Post\,'_{1k}}\dotcup
+ \mybigdotcup_{i=0}^{m_2}\set{\gamma'_{3i}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}\\
 &=
@@
 ~\quad\bigwedge_{i=0}^{m_3}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\Big)\\
-&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\&\qquad \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\Big)\\&\qquad
+&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\land\Pred^2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\&\qquad \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\Big)\\&\qquad
 \land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i\\&\qquad
@@
 ~\quad\bigwedge_{i=m+1}^{n}(\beta_{3{n'_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j=n'_i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\Big)\\
-&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\big)\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\&\qquad \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\Big)\\&\qquad
+&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\big)\land\Pred^2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\&\qquad \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\Big)\\&\qquad
 \land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i\\&\qquad
@@
 
+\TODO{prove the 3 theorems for composability of weak bisim or explain why the proof is similar to strong (thanks to the previous lemmas)}
 \newpage
@@
 \end{theorem}
- \begin{proof}  Consider $Q$ weak FH-bisimilar to $Q'$.
-It means that there exist a FH-bisimulation $\mathcal{R}_{Q,Q'}$ relating the two pNets $Q$ and $Q'$.
-We define a relation $\mathcal{R}$ relating states of $P[Q]_{j_0}$ with states of $P[Q']_{j_0}$:
-\[\mathcal{R} = \{(\ostate{S_P\uplus S_Q},\ostate{S_P\uplus S_{Q'}}, \Pred_{Q,Q'})|\,(S_Q,S_{Q'}, \Pred_{Q,Q'})\in\mathcal{R}_{Q,Q'}\}\]
-
-To prove weak FH-bisimulation of $\pNet[\pNetQ]_{j_0}$ and 
-	$\pNet[\pNetQ']_{j_0}$, we consider  an open transition $OT$ of $\pNet[\pNetQ]_{j_0}$, and an equivalent state of $\pNet[\pNetQ']_{j_0}$, and we try to find a family of WOT of 	$\pNet[\pNetQ']_{j_0}$ that simulates $OT$.
-Consider an OT of  $\pNet[\pNetQ]_{j_0}$ it is of the form (notations introduced to prepare the decomposition):
-\[
-\pNet[\pNetQ]_{j_0}\models\openrule
-	{
-		\beta_j^{j\in( J_P\uplus J_Q)}, 
-		\Pred_P\land \Pred_Q,  
-		\Post_P\uplus \Post_Q}
-	{\ostate{S_P\uplus S_Q} \OTWeakarrow {\alpha}
-		\ostate{S'_P\uplus S'_Q}
-}
-\]
-
-By the decomposition lemma for OTs (Lemma~\ref{lem-decompose}), we obtain the 2 following OTs (equality side-conditions have been inlined for clarity):
+ \begin{proof}  (Sketch of proof) Consider $Q$ weak FH-bisimilar to $Q'$.
+It means, according to Lemma  \ref{lem-alternative-weak-bisim} for any weak open transition $WOT$ in $Q$ there exist a family of weak open transitions $WOT_{x}^{x \in X}$ in $Q'$.
+We apply  Lemma \ref{lem-Weakcompose1} on weak open transition $WOT$, $j_0 \in J$, we obtain a new weak open transition $WOT'$ in $P[Q]_{j_0}$.
+On other hand, we apply same Lemma \ref{lem-Weakcompose1} on each weak open transitions $WOT_{x}$, so we obtain a new family of weak open transitions $WOT_{x}'$ in $P[Q']_{j_0}$.
+
+Suppose we have:\\[-2ex]
 \begin{mathpar}
 %\[
-\pNet\models{\openrule
-	{
-		\beta_j^{j\in J_P}\uplus(j_0\mapsto \alpha_Q), 
-		\Pred_P,  
-		\Post_Q}
-	{\ostate{S_P} \OTWeakarrow {\alpha}
-		\ostate{S'_P}}
+P\models{\openrule
+	{
+		\beta_j^{j\in J}, 
+		\Pred,  
+		\Post}
+	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
+		\ostate{(s_i')^{\, i\in L}}}
 }
@@
 
-By definition of $\mathcal{R}$ we have 
-$(S_Q,S_{Q'}| \Pred_{Q,Q'})\in\mathcal{R}_{Q,Q'}$. And thus, by definition of weak FH-bisimulation, there exist a family of weak open transitions $WOT_{x}$:
+Then, we have by lemma \ref{lem-Weakcompose}: \\[-2ex]
+	\[ P[Q]_{j_0}  
+	\models
+	{\openrule
+		{
+			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
+			\Pred\,',  \Post\,'
+			 }
+		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
+			\ostate{(s_i')^{\, i\in L\uplus L_Q}}}
+	}
+	\]
+
+On the other hand, $Q$ weak FH-bisimilar to $Q'$, so according to  Lemma  \ref{lem-alternative-weak-bisim} there exist a family of weak open transitions $WOT_{x}$:
  \begin{mathpar}
@@
          {
-           \gamma_{j x}^{j\in J_Q}, \Pred_{Q' x},\Post_{Q' x}}
-         {\ostate{S_{Q'}}\OTWeakarrow {\alpha_{x}} \ostate{S'_{Q' x}}}
+           \gamma_{j x}^{j\in J_{x}}, \Pred_{Q_x},\Post_{Q_x}}
+         {\ostate{t_{i}^{i\in L_{Q_x}}}\OTWeakarrow {\alpha_x} \ostate{t_{ix}^{i\in L_{Q_x}}}}
 \end{mathpar}
 
-where  
-\[\forall x.\, (S'_Q,S'_{Q' x}| \Pred_{Q,Q' x})\in\mathcal{R}_{Q,Q'}\]
-and
-\begin{equation*}
-\begin{split}
-\Pred_{Q,Q'}\land \Pred_Q \implies &
-\Big(\bigvee_{x\in X}
-(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x})\Rightarrow (\Pred_{Q_x}\land\\ &~~\alpha_Q=\alpha_x \land \Pred_{Q,Q' x}\subst{\Post_{Q' x}\uplus \Post_{Q}}) \Big)
-\end{split}
-\end{equation*}
-
-Composing the OT of $P$ with the WOTs of $Q'$ by Lemma~\ref{lem-Weakcompose1} we obtain:
-\[
-\pNet[\pNetQ']_{j_0}\models\openrule
-	{
-		\vis{\beta_j^{j\in( J_P}}\uplus\gamma_{j x}^{j\in J_Q}, 
-		\Pred_P\land \Pred_{Q' x},  
-		\Post_P\uplus \Post_{Q' x}}
-	{\ostate{S_P\uplus S_{Q'}} \OTWeakarrow {\alpha}
-		\ostate{S'_P\uplus S'_{Q' x}}
+such that...\\
+
+By applying  Lemma \ref{lem-Weakcompose} on each weak open transitions $WOT_{x}$, so we obtain a new family of weak open transitions $WOT_{x}'$ in $P[Q']_{j_0}$:
+
+\[ P[Q']_{j_0}  
+	\models
+	{\openrule
+		{
+			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
+			\Pred\,',  \Post\,'
+			 }
+		{\ostate{s_i^{i\in L} \uplus t_{i}^{i\in L_{Q_x}}} \OTWeakarrow {\alpha}
+			\ostate{(s_i')^{\, i\in L} \uplus t_{ix}^{i\in L_{Q_x}} }}
 	}
 	\]
-with $\bigvee_{x\in X}
-(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x} \implies \alpha_Q=\alpha_x$ that ensures that the open transitions can be recomposed when the OT fires.
-
-Side conditions necessary to prove weak-FH bisimulations are:
-
-\[\forall x.\, (S'_P\uplus S'_Q,S'_P\uplus S'_{Q' x}| \Pred_{Q,Q' x})\in\mathcal{R}\]
-which is trivially verified, and
-\begin{equation*}
-\begin{split}
-\Pred_{Q,Q'}\land \Pred_P\land \Pred_Q \implies &
-\Big(\bigvee_{x\in X}
-(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x}\land \forall j\in J_P.\, \vis{\beta_j}=\vis{\beta_j}))\Rightarrow\\
-& (\Pred_P\land \Pred_{Q' x}\land\\ &~~\alpha=\alpha \land \Pred_{Q,Q' x}\subst{\Post_P\uplus\Post_{Q' x}\uplus \Post_{Q}}) \Big)
-\end{split}
-\end{equation*}
-We conclude by observing that $\Post_P$ has no effect on variables of $Q$ and $Q'$, and thus on $\Pred_{Q,Q' x}$
-\qed
-
-% OLD
-% according to Lemma  \ref{lem-alternative-weak-bisim} for any weak open transition $WOT$ in $Q$ there exist a family of weak open transitions $WOT_{x}^{x \in X}$ in $Q'$. 
-%We apply  Lemma \ref{lem-Weakcompose1} on weak open transition $WOT$, $j_0 \in J$, we obtain a new weak open transition $WOT'$ in $P[Q]_{j_0}$.
-%On other hand, we apply same Lemma \ref{lem-Weakcompose1} on each weak open transitions $WOT_{x}$, so we obtain a new family of weak open transitions $WOT_{x}'$ in $P[Q']_{j_0}$.
-%
-%Suppose we have:\\[-2ex]
-%\begin{mathpar}
-%%\[
-%P\models{\openrule
-%	{
-%		\beta_j^{j\in J}, 
-%		\Pred,  
-%		\Post}
-%	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
-%		\ostate{(s_i')^{\, i\in L}}}
-%}
-%\quad\text{~~and~~}\quad
-%Q\models{\openrule
-%	{
-%		\set{\gamma},
-%		 \Pred_Q,  
-%		\Post_Q}
-%	{\ostate{s_{i}^{i\in L_Q}} \OTWeakarrow {\alpha_Q}
-%		\ostate{(s'_{i})^{\, i\in L_Q}}}
-%}%\]
-%
-%
-%\end{mathpar}
-%
-%Then, we have by lemma \ref{lem-Weakcompose}: \\[-2ex]
-%	\[ P[Q]_{j_0}  
-%	\models
-%	{\openrule
-%		{
-%			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
-%			\Pred\,',  \Post\,'
-%			 }
-%		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
-%			\ostate{(s_i')^{\, i\in L\uplus L_Q}}}
-%	}
-%	\]
-%
-%On the other hand, $Q$ weak FH-bisimilar to $Q'$, so according to  Lemma  \ref{lem-alternative-weak-bisim} 
-%
-%such that...\\
-%
-%By applying  Lemma \ref{lem-Weakcompose} on each weak open transitions $WOT_{x}$, so we obtain a new family of weak open transitions $WOT_{x}'$ in $P[Q']_{j_0}$:
-%
-%\[ P[Q']_{j_0}  
-%	\models
-%	{\openrule
-%		{
-%			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
-%			\Pred\,',  \Post\,'
-%			 }
-%		{\ostate{s_i^{i\in L} \uplus t_{i}^{i\in L_{Q_x}}} \OTWeakarrow {\alpha}
-%			\ostate{(s_i')^{\, i\in L} \uplus t_{ix}^{i\in L_{Q_x}} }}
-%	}
-%	\]
 
@@
 \end{theorem}
-
- \begin{proof}   Consider $P$ weak FH-bisimilar to $P'$.
-It means, there exist a FH-bisimulation $\mathcal{R}_{P,P'}$ relating the two pNets $P$ and $P'$.
-We define a relation $\mathcal{R}$ relating states of $P[Q]_{j_0}$ with states of $P'[Q]_{j_0}$:
-\[\mathcal{R} = \{(\ostate{S_P\uplus S_Q},\ostate{S_{P'}\uplus S_Q}, \Pred_{P,P'})|\,(S_P,S_{P'}, \Pred_{P,P'})\in\mathcal{R}_{P,P'}\}\]
-
-To prove weak FH-bisimulation of $\pNet[\pNetQ]_{j_0}$ and 
-	$\pNet'[\pNetQ]_{j_0}$, we consider  an open transition $OT$ of $\pNet[\pNetQ]_{j_0}$, and an equivalent state of $\pNet'[\pNetQ]_{j_0}$, and we try to find a family of WOT of 	$\pNet'[\pNetQ]_{j_0}$ that simulates $OT$.
-Consider an OT of  $\pNet[\pNetQ]_{j_0}$ it is of the form (notations introduced to prepare the decomposition):
-\[
-\pNet[\pNetQ]_{j_0}\models\openrule
-	{
-		\beta_j^{j\in( J_P\uplus J_Q)}, 
-		\Pred_P\land \Pred_Q,  
-		\Post_P\uplus \Post_Q}
-	{\ostate{S_P\uplus S_Q} \OTWeakarrow {\alpha}
-		\ostate{S'_P\uplus S'_Q}
-}
-\]
-
-By the decomposition lemma for OTs (Lemma~\ref{lem-decompose}), we obtain the 2 following OTs (equality side-conditions have been inlined for clarity):
-\begin{mathpar}
-%\[
-\pNet\models{\openrule
-	{
-		\beta_j^{j\in J_P}\uplus(j_0\mapsto \alpha_Q), 
-		\Pred_P,  
-		\Post_Q}
-	{\ostate{S_P} \OTWeakarrow {\alpha}
-		\ostate{S'_P}}
-}
-\quad\text{~~and~~}\quad
-Q\models{\openrule
-	{
-		\beta_j^{j\in J_Q},
-		 \Pred_Q,  
-		\Post_Q}
-	{\ostate{S_Q} \OTWeakarrow {\alpha_Q}
-		\ostate{S'_Q}}
-}%\]
-
-\end{mathpar}
-
-By definition of $\mathcal{R}$ we have 
-$(S_P,S_{P'}, \Pred_{P,P'})\in\mathcal{R}_{P,P'}$. And thus, by definition of weak FH-bisimulation, there exist a family of weak open transitions $WOT_{x}$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j x}^{j\in J_P\uplus\{j_0\}}, \Pred_{P' x},\Post_{P' x}}
-         {\ostate{S_{P'}}\OTWeakarrow {\alpha_{x}} \ostate{S'_{P' x}}}
-\end{mathpar}
-
-where  
-\[\forall x.\, (S'_P,S'_{P' x}, \Pred_{P,P' x})\in\mathcal{R}_{P,P'}\]
-and
-\begin{equation*}
-\begin{split}
-\Pred_{P,P'}\land \Pred_P \implies &
-\Big(\bigvee_{x\in X}
-(\forall j\in J_P.\, \vis{\beta_j}=\gamma_{j x} \land \vis{\alpha_Q}=\gamma_{j_0})\Rightarrow (\Pred_{Q_x}\land\\ &~~\alpha=\alpha_x \land \Pred_{P,P' x}\subst{\Post_{P' x}\uplus \Post_{P}}) \Big)
-\end{split}
-\end{equation*}
-
-We here need a special case of Lemma\ref{lem-Weakcompose}where the inner pNet $Q$ does a simple OT.
-This is just a particular case of the theorem but where notations get simplified because the inner pnet does a single transition.
- This way we can compose the WOTs of $P'$ with the OT of $Q$ and obtain, whenever $\vis{\beta_j}=\gamma_{j x} $:
-\[
-\pNet'[\pNetQ]_{j_0}\models\openrule
-	{
-		\vis{\beta_j^{j\in( J_Q}}\uplus\gamma_{j x}^{j\in J_Q}, 
-		\Pred_{P' x}\land \Pred_Q,  
-		\Post_{P' x}\uplus \Post_Q}
-	{\ostate{S_{P'}\uplus S_{Q}} \OTWeakarrow {\alpha_x}
-		\ostate{{S'_{P' x}}\uplus S'_Q}
-}
-\]
-Side conditions necessary to prove weak-FH bisimulations are:
-
-\[\forall x.\, (S'_P\uplus S'_Q,S'_{P' x}\uplus S'_Q, \Pred_{P,P' x})\in\mathcal{R}\]
-which is trivially verified, and
-\begin{equation*}
-\begin{split}
-\Pred_{P,P'}\land \Pred_P\land \Pred_Q \implies &
-\Big(\bigvee_{x\in X}
-(\forall j\in J_P.\, \vis{\beta_j}\gamma_{j x} \land \forall j\in J_Q.\, \vis{\beta_j}=\vis{\beta_j} )\Rightarrow\\
-& (\Pred_{P' x}\land \Pred_Q\land\\ &~~\alpha_x=\alpha \land \Pred_{P,P' x}\subst{\Post_{P' x}\uplus\Post_P\uplus \Post_{Q}}) \Big)
-\end{split}
-\end{equation*}
-We conclude by observing that $\Post_Q$ has no effect on variables of $P$ and $P'$, and thus on $\Pred_{P,P' x}$
-\qed
-\end{proof}
+\newpage
+
+\section{Full details of the Simple Protocol Example}
+
+Let us start with the basic version, with no error counter.
+
+\begin{figure}[t]
+   \includegraphics[width=5.5cm]{XFIG/SimpleProt-Schema}
+   \includegraphics[width=6.5cm]{XFIG/SimpleProt-Spec}
+   \caption{Specification pNet Schema and Specification}
+   \label{SimpleProt:Spec}
+
+\end{figure}
+
+\begin{figure}[t]
+  \centerline{\includegraphics[width=12cm]{XFIG/SimpleProt-pNet}}
+  \caption{Composed pNet with the Simple Protocol Implementation}  \label{SimpleProt:Impl}
+\end{figure}
 
 \end{document}
+
 \section{Examples of Lotos laws}

### 2019-10-17 2016-Weak-FH-Bisim/WeakBisim.tex

--- 2019-10-16 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
+Fig. \ref{SimpleProt:Spec} shows the Schema of this system, and on the right side, its global specification, expressed as a pNet. 
+The full system should be equivalent (e.g. through weak bisimulation)
+to the two processes connected simply through a perfect medium. Fig. \ref{SimpleProt:Spec}, right, shows the pNet representing this global specification.
+
 Fig.
-\ref{SimpleProt:Spec} shows the Schema of this system, and on the right side, its global specification, expressed as a pNet: it should be equivalent to a simple system where the holes would be connected by a perfect reliable medium.
-
-The full system should be equivalent (e.g. through weak bisimulation)
-to the two processes connected simply through a perfect medium.
+\ref{SimpleProt:Impl} show the pNet model of the protocol.
+When the medium detects an error (modeled by a local $\tau$ action), it sends back a $m\_error$ message to the $Sender$.
+The $Sender$ increments its error counter $c$, and resend the message (including $c$) to the medium, that will, eventually, transmit $m,c$ to the receiver.
 
 \section{A model of process composition}\label{sec:OT}
-\TODO{Commenter la figure 2}
 
@@
 
+\newpage
+
+\section{Full details of the Simple Protocol Example}
+
+Let us start with the basic version, with no error counter.
+
+\begin{figure}[t]
+   \includegraphics[width=5.5cm]{XFIG/SimpleProt-Schema}
+   \includegraphics[width=6.5cm]{XFIG/SimpleProt-Spec}
+   \caption{Specification pNet Schema and Specification}
+   \label{SimpleProt:Spec}
+
+\end{figure}
+
+\begin{figure}[t]
+  \centerline{\includegraphics[width=12cm]{XFIG/SimpleProt-pNet}}
+  \caption{Composed pNet with the Simple Protocol Implementation}  \label{SimpleProt:Impl}
+\end{figure}
+
 \end{document}
+
 \section{Examples of Lotos laws}

### 2019-10-17 2016-Weak-FH-Bisim/WeakBisim.tex
Def OT

@@
 \subsection{Open Automata}
- Open automata are not composition structures but they are made of transitions that are dependent of the actions of the holes, and they can reason on variables (potentially with only symbolic values).
+ Open automata (OA) are not composition structures but they are made of transitions that are dependent of the actions of the holes, and they can reason on variables (potentially with only symbolic values).
+Formaly, each state of an OA has set of \emph{state variables}, and all state variable sets are disjoint.
 %\TODO{adopt a uniform notation for open transitions, almost each instance has a 
@@
 	\label{def:OpenTransitions}
-	An \emph{open transition} over a
+	An \emph{open transition} (OT) over a
 	set $J$ of holes with sorts $\Sort_j^{j\in J}$ and a set of states $\mathcal{S}$ is 
@@
         is a transition of the hole $j$, with $\beta_j\in\Sort_j$. $\alpha$ is an action 
-        label denoting the resulting action
-        of this open transition. \Pred\ is a predicate 
-	over the different variables of the
-	terms, labels, and states $\beta_j$, $s$, $\alpha$. \Post\ is a set of 
-	equations 
-	that 
-	hold \emph{after the open transition}, they are represented as a substitution of the 
-	form $({x_k\gets e_k})^{k\in K}$ 
-	where $x_k$ are variables of $s'$, and $e_k$ are expressions over the other 
-	variables of the open transition. Open transitions are identified modulo logical equivalence on their predicate.
+        label denoting the resulting action of this open transition.
+        We call \emph{source variables} of an OT the union of all variables
+        in the different terms
+        $\beta_j$ and $\alpha$, and the state variables of $s$.
+        \Pred\ is a predicate over the source variables. \Post\ is a set of 
+	equations that hold \emph{after the open transition}, they are
+        represented as a substitution of the form $({x_k\gets e_k})^{k\in K}$ 
+	where $x_k$ are state variables of $s'$, and $e_k$ are expressions
+        over the source variables. Open transitions are identified
+        modulo logical equivalence on their predicate. 
 \end{definition}
@@
 
-We take in this article a semantics and logical understanding of these automata.
-Open automata are closed by a simple form of refinement that allows us to refine the predicate, or substitute any free variable by an expression.
-More formally, let $\Post$ be any substitution and $\Pred$ any predicate suppose $\vars(t)\cap \dom(\Post)=\emptyset$ and $\vars(t')\cap \dom(\Post)=\emptyset$.
-Then we have the following implication:
+We take in this article a semantics and logical understanding of these
+automata. Open automata are closed by a simple form of refinement that
+allows us to refine the predicate, or substitute any free variable by
+an expression. More formally, let $\Post$ be any substitution and
+$\Pred$ any predicate suppose $\vars(t)\cap \dom(\Post)=\emptyset$ and
+$\vars(t')\cap \dom(\Post)=\emptyset$. Then we have the following
+implication:
 
@@
 
-Another consequence of the semantics and logical interpretation of the formulas is that we make no distinction between the equality and the equivalence on boolean formulas, i.e.
-equivalence of two predicates $\Pred$ and $\Pred\,'$ can be denoted $\Pred=\Pred\,'$.
+Another consequence of the semantics and logical interpretation of the
+formulas is that we make no distinction between the equality and the
+equivalence on boolean formulas, i.e. equivalence of two predicates
+$\Pred$ and $\Pred\,'$ can be denoted $\Pred=\Pred\,'$.
 

### 2019-10-21 2016-Weak-FH-Bisim/WeakBisim.tex
typo in OT Def
related bib

@@
 
-- TROUVER UN EXEMPLE ET LE METTRE DANS L ARTICLE
-
 - enlever 5.2 et citer avocs
@@
 implies blablabla
-
-- adopter la def semantique d ot pour la bisim
 
@@
 
-Fig. \ref{SimpleProt:Schema} shows the example principle: two unspecified
+Fig. \ref{SimpleProt:Spec} (left) shows the example principle: two unspecified
 processes $P$ and $Q$ (Holes) communicate messages, with a data value
@@
 
-Fig. \ref{SimpleProt:Spec} shows the Schema of this system, and on the right side, its global specification, expressed as a pNet. 
+Fig. \ref{SimpleProt:Spec} (right) shows the Schema of this system, and on the right side, its global specification, expressed as a pNet. 
 The full system should be equivalent (e.g. through weak bisimulation)
@@
 	\end{mathpar}
-	Where $J'\subseteq$, $s, s'\in\mathcal{S}$ and $\beta_j$
+	Where $J'\subseteq J$, $s, s'\in\mathcal{S}$ and $\beta_j$
         is a transition of the hole $j$, with $\beta_j\in\Sort_j$. $\alpha$ is an action 
@@
 
-The proof of this theorem can be found in Appendix~\ref{thm-equiv-proof}.
+The proof of this theorem can be found in~\ref{thm-equiv-proof}.
 The only non-trivial part of the proof is the proof of transitivity.
@@
 
-\TODO{rertavailler le paragraphe ci dessous}
+\TODO{retravailler le paragraphe ci dessous}
 In
@@
 One major different however is that pNets in their current state are not much adapted to probabilistic verification contrarily to \cite{Johnson:2014:qosa} but they are better suited to verify complex behavioural properties.
+
+\ERIC{J'ai copie/colle ici le Related Work que Zechen a mis dans notre
+  papier bisim...
+  Pas tres satisfaisant pour les aspects Weak, mais quelques inputs a
+  regarder}
+
+To the best of our knowledge, there is no other research works on the Bisimulation Equivalence between such complicate(open, symbolic, parameterized, with loops and assignments) system models, with providing fully complete algorithms.
+For the sake of completeness, we give a brief overview of other Symbolic Bisimulation researches.
+
+One line of research is providing Symbolic Bisimulation for different model or language. 
+In Calder's work\cite{calder2001symbolic}, they define a symbolic semantic for full LOTOS, with a symbolic bisimulation over it;
+Borgstrom et al., Delaune et al.
+and Buscemi et al.
+provide symbolic semantic and equivalence for different variants of pi calculus respectively\cite{borgstrom2004symbolic}\cite{delaune2007symbolic}\cite{buscemi2008open}, and later in 2012 Liu's work provided symbolic bisimulation  for full applied pi calculus\cite{liu2010complete};
+The most recent work, Feng et al. provide a symbolic bisimulation for quantum processes
+\cite{feng2014symbolic}.
+All the above works, didn't give a complete approach for verification, and the models on which these works based are simpler or different than ours.
+
+Another line of research is devising the algorithm for computing symbolic Bisimulation Equivalence.
+In Dovier's work, they provide a rank-based algorithm, layering the input model to compute bisimulation\cite{dovier2002rank}. 
+Baldan et al. also focus on open systems, using a logical programming language \emph{Prolog} to model the systems and compute Bisimulation\cite{baldan2001compositional}.
+Wimmer et al. present a signature-based approach to compute Bisimulation, implemented by using BDDs\cite{wimmer2006sigref}.
+Lin present a symbolic bisimulation between symbolic transition graph with assignments(STGA), as mentioned in \emph{Introduction}, bring us lots of inspirations.
 
@@
 
-\NOTE{Eric: one transition of the <020> table, from the draft on my white board}
+\NOTE{ERIC: one transition of the <020> table, from the draft on my white board}
 

### 2019-10-21 2016-Weak-FH-Bisim/WeakBisim.tex
Example code in Appendix

@@
 \usepackage{hyperref}
+\usepackage{listings}
+\lstset{basicstyle=\small}
 
@@
 
-Let us start with the basic version, with no error counter.
-
 \begin{figure}[t]
@@
 \end{figure}
+
+The first piece of code is the textual definition of the SimpleProtSec
+pNet. This code should be intuitive enough to read, with the following
+conventions:
+
+\begin{itemize}
+  \item Constants of any type (including Action) must be declared as
+    ``const''. They are used either as functions with argument, as
+    typically \texttt{in(msg)}, or constants without argument, denoted
+    as \texttt{\$tau}. Identifiers without the ``?'' marker are
+    variables.
+  \item Variables can be declared either: inside a pLTS state (normal
+    state variable), as global variable of a pLTS (see e.g. ...), or
+    as an input variable in a transition, as \texttt{?msg} in pLTS M1
+    here.
+  \item \TODO{continue...}
+\end{itemize}
+
+\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
+SimpleProtSpec2:
+import "Data_Alg.algp"
+root SimpleProtSpec2
+const in, out:Action
+const p_send, q_recv: Action
+const tau:Action
+
+pLTS M1
+initial a0
+vars ?msg:Data
+
+state a0
+transition in(msg) -> a1 {a1_msg:=msg}
+
+state a1
+vars a1_msg:Data {m1_c:=0}:Int
+
+transition out(a1_msg, m1_c) -> a0
+transition synchro($tau)  -> a1 {m1_c:=m1_c+1}
+
+pNet SimpleProtSpec2
+holes P,Q
+subnets P,M1,Q
+vars p_a,q_a:Action m:Data c:Int
+
+vector SV0 <p_send(m), in(m),_>->p_send(m)
+vector SV1 <p_a,_,_>->p_a [p_a != p_send(m)]
+vector SV2 <_, out(m,c), q_recv(m)>->q_recv(m,c)
+vector SV3 <_,_,q_a>->q_a [q_a != q_recv(m)]
+
+  \end{lstlisting}
+
+The corresponding generated Open Automaton was given in Figure \ref{},
+page \pageref{}.
+
+Next is the code for the SimpleProtImpl pNet:
+
+\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
+SimpleProtImpl:
+import "Data_Alg.algp"
+
+root SimpleProtImpl2
+
+const in,out:Action
+const tau,p_send,q_recv,m_recv,m_send,m_error: Action
+const s_send,s_ack,s_error,r_recv,r_ack: Action
+
+pLTS M1
+initial a0
+vars ?msg:Data ?c:Int
+
+state a0
+transition m_recv(msg,c) -> a1 {a1_msg:=msg, a1_c:=c}
+
+state a1
+vars a1_msg:Data a1_c:Int
+transition m_send(a1_msg, a1_c) -> a0 
+transition synchro($tau) -> a2
+
+state a2
+transition $m_error -> a0
+
+pLTS Sender
+initial s0
+vars ?msg:Data
+
+state s0
+transition in(msg) -> s1 {s1_msg:=msg, s1_c:=0}
+
+state s1
+vars s1_msg:Data s1_c:Int
+transition s_send(s1_msg, s1_c) -> s2
+
+state s2
+vars  s2_c:Int
+transition $s_ack -> s0
+transition $s_error -> s1 {s1_c:=s2_c+1}
+
+pLTS Receiver
+initial r0
+vars ?msg:Data ?c:Int
+
+state r0
+transition r_recv(msg,c) -> r1 {r1_msg:=msg, r1_c:=c}
+
+state r1
+vars r1_msg:Data r1_c:Int
+transition out(r1_msg, r1_c) -> r2
+
+state r2
+transition $r_ack -> r0
+
+pNet medium
+subnets Sender, M1, Receiver
+vars m:Data c:Int
+vector SV0 <in(m), _, _>->in(m)
+vector SV1 <s_send(m,c), m_recv(m,c), _>->synchro($tau)
+vector SV2 <_, m_send(m), r_recv(m)>->synchro($tau)
+vector SV3 <$s_ack, _, $r_ack>->synchro($tau)
+vector SV4 <$s_error, $m_error, _>->synchro($tau)
+vector SV5 <_, _, out(m,c)>->out(m,c)
+
+pNet SimpleProtImpl2
+holes P,Q
+subnets P,medium,Q
+vars p_a,q_a:Action  m:Data c:Int
+vector SV0 <p_send(m), in(m),_>->in(m)
+vector SV1 <p_a,_,_>->p_a [p_a != p_send(m)]
+vector SV2 <_, out(m,c), q_recv(m,c)>->out(m,c)
+vector SV3 <_,_,q_a>->q_a [q_a != q_recv(m,c)]
+\end{lstlisting}
+
+From this code,A more compact view (maybe more readable ???) is given
+by the pretty-printer of VerCors:
+
+\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
+SimpleProtImpl2
+--------------------
+SV6 SVs: <p_send(m), in(m), _>-->in(m)
+SV7 SVs: <p_a, _, _>-->p_a, p_a!=(p_send(m))
+SV8 SVs: <_, out(m, c), q_recv(m, c)>-->out(m, c)
+SV9 SVs: <_, _, q_a>-->q_a, q_a!=(q_recv(m, c))
+SV11 SVs: <_, _tau_, _>-->_tau_
+SV12 SVs: <_, _tau_, _>-->_tau_
+SV13 SVs: <_, _tau_, _>-->_tau_
+SV14 SVs: <_, _tau_, _>-->_tau_
+SV15 SVs: <_, _tau_, _>-->_tau_
+Holes: P
+Subnets: medium
+- medium
+- SV0 SVs: <in(m), _, _>-->in(m)
+- SV1 SVs: <s_send(m, c), m_recv(m, c), _>-->_tau_
+- SV2 SVs: <_, m_send(m), r_recv(m)>-->_tau_
+- SV3 SVs: <s_ack, _, r_ack>-->_tau_
+- SV4 SVs: <s_error, m_error, _>-->_tau_
+- SV5 SVs: <_, _, out(m, c)>-->out(m, c)
+- SV10 SVs: <_, _tau_, _>-->_tau_
+- pLTS: Sender
+- - Transition: s0---in(msg)-->s1, { s1_msg := msg s1_c := 0}
+- - Transition: s1---s_send(s1_msg, s1_c)-->s2, {}
+- - Transition: s2---s_ack-->s0, {}
+- - Transition: s2---s_error-->s1, { s1_c := s2_c+1}
+- - Variable: s1_c, State: s1, Value(s) = 0,s2_c+1,
+- - Variable: s1_msg, State: s1, Value(s) = msg,
+- pLTS: M1
+- - Transition: a0---m_recv(msg, c)-->a1, { a1_msg := msg a1_c := c}
+- - Transition: a1---m_send(a1_msg, a1_c)-->a0, {}
+- - Transition: a1---_tau_-->a2, {}
+- - Transition: a2---m_error-->a0, {}
+- - Variable: a1_msg, State: a1, Value(s) = msg,
+- - Variable: a1_c, State: a1, Value(s) = c,
+- pLTS: Receiver
+- - Transition: r0---r_recv(msg, c)-->r1, { r1_msg := msg r1_c := c}
+- - Transition: r1---out(r1_msg, r1_c)-->r2, {}
+- - Transition: r2---r_ack-->r0, {}
+- - Variable: r1_msg, State: r1, Value(s) = msg,
+- - Variable: r1_c, State: r1, Value(s) = c,
+Holes: Q
+\end{lstlisting}
+
+Finaly, we list here, in raw format, the 24 OTs computed by the tool:
+
+\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
+INFO  SimpleProtImpl2 - Total: 24 OTs
+INFO  SimpleProtImpl2 - 
+		{P|->p_send(m:sva_SV6:1:1)},   [((in(msg))=:ra:Sender:121:1)/\(:ra:Sender:121:1=(in(m:sva_SV0:12:1)))/\((in(m:sva_SV0:12:1))=(in(m:sva_SV6:1:1)))],   {s1_msg := msg, s1_c := 0}
+	OT:1 ------------------------------------------------------------
+		<s0_a0_r0>-----in(m:sva_SV6:1:1)----><s1_a0_r0>
+
+INFO  SimpleProtImpl2 - 
+		{P|->p_a:sva_SV7:1:2},   [(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
+	OT:2 ------------------------------------------------------------
+		<s0_a0_r0>-----p_a:sva_SV7:1:2----><s0_a0_r0>
+
+INFO  SimpleProtImpl2 - 
+		{Q|->q_a:sva_SV9:1:4},   [(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
+	OT:3 ------------------------------------------------------------
+		<s0_a0_r0>-----q_a:sva_SV9:1:4----><s0_a0_r0>
+
+INFO  SimpleProtImpl2 - 
+		{P|->p_a:sva_SV7:1:2},   [(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
+	OT:4 ------------------------------------------------------------
+		<s1_a0_r0>-----p_a:sva_SV7:1:2----><s1_a0_r0>
+
+INFO  SimpleProtImpl2 - 
+		{Q|->q_a:sva_SV9:1:4},   [(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
+	OT:5 ------------------------------------------------------------
+		<s1_a0_r0>-----q_a:sva_SV9:1:4----><s1_a0_r0>
+
+INFO  SimpleProtImpl2 - 
+		{},   [((s_send(s1_msg, s1_c))=:ra:Sender:1144:1)/\(:ra:Sender:1144:1=(s_send(m:sva_SV1:114:2, c:sva_SV1:114:2)))/\((m_recv(msg, c))=:ra:M1:1145:1)/\(:ra:M1:1145:1=(m_recv(m:sva_SV1:114:2, c:sva_SV1:114:2)))/\(_tau_=_tau_)],   {a1_msg := msg, a1_c := c}
+	OT:6 ------------------------------------------------------------
+		<s1_a0_r0>-----_tau_----><s2_a1_r0>
+
+INFO  SimpleProtImpl2 - 
+		{},   [((s_send(s1_msg, s1_c))=:ra:Sender:1174:1)/\(:ra:Sender:1174:1=(s_send(m:sva_SV1:117:2, c:sva_SV1:117:2)))/\((m_recv(msg, c))=:ra:M1:1175:1)/\(:ra:M1:1175:1=(m_recv(m:sva_SV1:117:2, c:sva_SV1:117:2)))/\(_tau_=_tau_)],   {a1_msg := msg, a1_c := c}
+	OT:7 ------------------------------------------------------------
+		<s1_a0_r0>-----_tau_----><s2_a1_r0>
+
+INFO  SimpleProtImpl2 - 
+		{},   [((s_send(s1_msg, s1_c))=:ra:Sender:1204:1)/\(:ra:Sender:1204:1=(s_send(m:sva_SV1:120:2, c:sva_SV1:120:2)))/\((m_recv(msg, c))=:ra:M1:1205:1)/\(:ra:M1:1205:1=(m_recv(m:sva_SV1:120:2, c:sva_SV1:120:2)))/\(_tau_=_tau_)],   {a1_msg := msg, a1_c := c}
+	OT:8 ------------------------------------------------------------
+		<s1_a0_r0>-----_tau_----><s2_a1_r0>
+
+INFO  SimpleProtImpl2 - 
+		{},   [((s_send(s1_msg, s1_c))=:ra:Sender:1234:1)/\(:ra:Sender:1234:1=(s_send(m:sva_SV1:123:2, c:sva_SV1:123:2)))/\((m_recv(msg, c))=:ra:M1:1235:1)/\(:ra:M1:1235:1=(m_recv(m:sva_SV1:123:2, c:sva_SV1:123:2)))/\(_tau_=_tau_)],   {a1_msg := msg, a1_c := c}
+	OT:9 ------------------------------------------------------------
+		<s1_a0_r0>-----_tau_----><s2_a1_r0>
+
+INFO  SimpleProtImpl2 - 
+		{},   [((s_send(s1_msg, s1_c))=:ra:Sender:1264:1)/\(:ra:Sender:1264:1=(s_send(m:sva_SV1:126:2, c:sva_SV1:126:2)))/\((m_recv(msg, c))=:ra:M1:1265:1)/\(:ra:M1:1265:1=(m_recv(m:sva_SV1:126:2, c:sva_SV1:126:2)))/\(_tau_=_tau_)],   {a1_msg := msg, a1_c := c}
+	OT:10 ------------------------------------------------------------
+		<s1_a0_r0>-----_tau_----><s2_a1_r0>
+
+INFO  SimpleProtImpl2 - 
+		{P|->p_a:sva_SV7:1:2},   [(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
+	OT:11 ------------------------------------------------------------
+		<s2_a1_r0>-----p_a:sva_SV7:1:2----><s2_a1_r0>
+
+INFO  SimpleProtImpl2 - 
+		{Q|->q_a:sva_SV9:1:4},   [(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
+	OT:12 ------------------------------------------------------------
+		<s2_a1_r0>-----q_a:sva_SV9:1:4----><s2_a1_r0>
+
+INFO  SimpleProtImpl2 - 
+		{},   [(_tau_=:ra:M1:11420:1)/\(:ra:M1:11420:1=_tau_)/\(_tau_=_tau_)],   {}
+	OT:13 ------------------------------------------------------------
+		<s2_a1_r0>-----_tau_----><s2_a2_r0>
+
+INFO  SimpleProtImpl2 - 
+		{},   [(_tau_=:ra:M1:11720:1)/\(:ra:M1:11720:1=_tau_)/\(_tau_=_tau_)],   {}
+	OT:14 ------------------------------------------------------------
+		<s2_a1_r0>-----_tau_----><s2_a2_r0>
+
+INFO  SimpleProtImpl2 - 
+		{},   [(_tau_=:ra:M1:12020:1)/\(:ra:M1:12020:1=_tau_)/\(_tau_=_tau_)],   {}
+	OT:15 ------------------------------------------------------------
+		<s2_a1_r0>-----_tau_----><s2_a2_r0>
+
+INFO  SimpleProtImpl2 - 
+		{},   [(_tau_=:ra:M1:12320:1)/\(:ra:M1:12320:1=_tau_)/\(_tau_=_tau_)],   {}
+	OT:16 ------------------------------------------------------------
+		<s2_a1_r0>-----_tau_----><s2_a2_r0>
+
+INFO  SimpleProtImpl2 - 
+		{},   [(_tau_=:ra:M1:12620:1)/\(:ra:M1:12620:1=_tau_)/\(_tau_=_tau_)],   {}
+	OT:17 ------------------------------------------------------------
+		<s2_a1_r0>-----_tau_----><s2_a2_r0>
+
+INFO  SimpleProtImpl2 - 
+		{P|->p_a:sva_SV7:1:2},   [(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
+	OT:18 ------------------------------------------------------------
+		<s2_a2_r0>-----p_a:sva_SV7:1:2----><s2_a2_r0>
+
+INFO  SimpleProtImpl2 - 
+		{Q|->q_a:sva_SV9:1:4},   [(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
+	OT:19 ------------------------------------------------------------
+		<s2_a2_r0>-----q_a:sva_SV9:1:4----><s2_a2_r0>
+
+INFO  SimpleProtImpl2 - 
+		{},   [(s_error=:ra:Sender:11413:1)/\(:ra:Sender:11413:1=s_error)/\(m_error=:ra:M1:11414:1)/\(:ra:M1:11414:1=m_error)/\(_tau_=_tau_)],   {s1_c := s2_c+1}
+	OT:20 ------------------------------------------------------------
+		<s2_a2_r0>-----_tau_----><s1_a0_r0>
+
+INFO  SimpleProtImpl2 - 
+		{},   [(s_error=:ra:Sender:11713:1)/\(:ra:Sender:11713:1=s_error)/\(m_error=:ra:M1:11714:1)/\(:ra:M1:11714:1=m_error)/\(_tau_=_tau_)],   {s1_c := s2_c+1}
+	OT:21 ------------------------------------------------------------
+		<s2_a2_r0>-----_tau_----><s1_a0_r0>
+
+INFO  SimpleProtImpl2 - 
+		{},   [(s_error=:ra:Sender:12013:1)/\(:ra:Sender:12013:1=s_error)/\(m_error=:ra:M1:12014:1)/\(:ra:M1:12014:1=m_error)/\(_tau_=_tau_)],   {s1_c := s2_c+1}
+	OT:22 ------------------------------------------------------------
+		<s2_a2_r0>-----_tau_----><s1_a0_r0>
+
+INFO  SimpleProtImpl2 - 
+		{},   [(s_error=:ra:Sender:12313:1)/\(:ra:Sender:12313:1=s_error)/\(m_error=:ra:M1:12314:1)/\(:ra:M1:12314:1=m_error)/\(_tau_=_tau_)],   {s1_c := s2_c+1}
+	OT:23 ------------------------------------------------------------
+		<s2_a2_r0>-----_tau_----><s1_a0_r0>
+
+INFO  SimpleProtImpl2 - 
+		{},   [(s_error=:ra:Sender:12613:1)/\(:ra:Sender:12613:1=s_error)/\(m_error=:ra:M1:12614:1)/\(:ra:M1:12614:1=m_error)/\(_tau_=_tau_)],   {s1_c := s2_c+1}
+	OT:24 ------------------------------------------------------------
+		<s2_a2_r0>-----_tau_----><s1_a0_r0>
+
+INFO  SimpleProtImpl2 - Total: 24 SATISFIABLE OTs
+INFO  SimpleProtImpl2 -        278 UNSATISFIABLE OTs
+INFO  SimpleProtImpl2 - Total Time: 1056 ms
+
+\end{lstlisting}
 

### 2019-10-24 2016-Weak-FH-Bisim/WeakBisim.tex
redaction dans sec 5.4,5.3

@@
 \subsection{Composition properties: composition of weak open transitions}
-Now the semantics of an open pNet is defined both as an open automaton, and as a weak open automaton.
+We now have two different semantics for open pNets: a stronf semantics, defined  as an open automaton, and as a weak semantics, defined as a weak open automaton.
 Like the open automaton, the weak open automaton features valuable composition properties.
 We can exhibit  a composition property and a decomposition property that relate open pNet composition with their semantics, defined as weak open automata.
-These are technically more complex than the ones for open automata because each hole performs a set of actions, and thus a composed transition is the composition of one transition of the top-level pNet and a sequence of transitions of the sub-pnet that fills its hole.
+These are however technically more complex than the ones for open automata because each hole performs a set of actions, and thus a composed transition is the composition of one transition of the top-level pNet and a sequence of transitions of the sub-pNet that fills its hole.
+They can be found as Lemmas~\ref{lem-decomposeWOT}, Lemma~\ref{lem-Weakcompose1}, and Lemma~\ref{lem-Weakcompose} in~\ref{sec:app-composition}.
 
 \subsection{Weak FH-bisimulation}
+For defining a bisimulaiton relation between weak open automatas, two options are possible.
+Either we define a simulation similar to the strong simulation but based on open automata, this would look like the FH-simulation but would need to be adapted to weak open transitions.
+Or we define directly and classically a weak FH-simulation as a relation between two open automata, relating the open transition of one open automaton with the transition of the weak open automaton derived from the second one.
+
+The definition below specifies how a set of weak open transitions can simulate an open transition, and under which condition; this is used to relate, by weak FH-bisimulation, two open automata by reasoning on the weak open automata that can be derived from the strong ones.
+This is defined formally as follows.
 
@@
 
-Weak bisimulation can be alternatively defined as a strong bisimulation on the weak open automata, however this would still need a specific definition of strong bisimulation for weak open automata.
-\TODO{polish}
+Compared to strong bisimulation, except the obvious use of weak open transitions to simulate an open transition, the condition on predicate is slightly changed concerning actions of the holes.
+Indeed only the visible actions of the holes must be compared and they form a list of actions, but of length at most one.
+
+Weak FH-bisimilarity is an equivalence in the same way as strong FH-bisimilarity.
 
@@
 \end{theorem}
-proof in appendix
+The proof  is detailed in \ref{app-WFH-equiv}, it follows a similar pattern as the proof that strong FH-bisimulation is an equivalence, but technical details are different, and in practice we rely on a different (but proven equivalent) definition of weak FH-bisimilarity; this equivalent version simulates a \emph{weak} open transition with a set of weak open transition.
+The careful use of the best definition of weak FH-bisimilarity makes the proof similar to the strong FH-bisimulation case.
 
@@
 
-\subsection{Weak bisimulation is an equivalence}
+\subsection{Weak bisimulation is an equivalence}\label{app-WFH-equiv}
 
@@
 
-\subsection{Composition properties}
+\subsection{Composition properties}\label{sec:app-composition}
 This section gives detailed lemmas and their proofs, these are the equivalent of the composition lemmas for open transitions, but applied to weak automata that give the semantics of open pNets.

### 2019-10-25 2016-Weak-FH-Bisim/WeakBisim.tex
notation + ajout refs

@@
 \TODO{Rabea: trouver reference !!}
-To illustrate this work, we use a simple transport protocol, that provides safe transport of data between two processes,
-over unsafe media.
+To illustrate this work, we use a simple communication protocol, that provides safe transport of data between two processes, over unsafe media.
+The alternating bit protocol was first described in \cite{Bartlett:1969}.
+Our specification  of the ABP is based on the one given in \cite{Vergamini:1986}.
 
@@
  \noindent                        
- \begin{small} $\Pred_{s,t} \land \Pred_{OT}\\ 
+ \begin{small} $\Pred_{s,t} \land \Pred_{OT} 
  \implies 	\Pred_{s,t}\land\Pred\,'\land \Pred\,''\land\alpha_Q=\beta_{j_0}\\ % 
@@
  	\land \alpha_Q\!=\!\alpha_x \land  
- 	\Pred_{s x}\subst{\Post\,''\uplus\Post_{OT_x}}\right)\land
- }
- \\~\qquad\quad \Pred\,'\land\alpha_Q=\beta_{j_0} \\
+ 	\Pred_{s,x}\subst{\Post\,''\uplus\Post_{OT_x}}\right)\land
+ }
+ \\ \Pred\,'\land\alpha_Q=\beta_{j_0} \\
  	\implies
@@
  		\land \alpha_Q\!=\!\alpha_x \land \alpha_Q\!=\!\beta_{j_0 x}\, \land} \\ 
- 	~\qquad\quad 	\Pred_{s, x}\subst{\Post\,''\uplus\Post_{OT_x}})
+ 		\Pred_{s, x}\subst{\Post\,''\uplus\Post_{OT_x}})
  	 $\end{small}
@@
  	$\Pred_{s x}\subst{(\Post\,'\uplus 	\Post\,'')\uplus(\Post\,'\uplus \Post_{OT_x})}$. We 
- 	can conclude by observing that	$\Pred_{s x}$ does not use any variable of $P$ 
+ 	can conclude by observing that	$\Pred_{s,x}$ does not use any variable of $P$ 
  	and thus the substitution $\subst{Post\,'}$ has no effect on it.
@@
 \begin{small} 
-$\Pred_{s,t} \land \Pred_{OT}\\ \implies
+$\Pred_{s,t} \land \Pred_{OT} \implies
  \Pred_{s,t}\land\Pred\,'\land \Pred\,''\land \alpha_Q=\beta_{j_0}\\  
@@
 $
-\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\!\!\Post_j^1}}\\
+\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\!\!\Post_{1j}}}\\
 s''=s_{10} \wedge s_{1(n+2)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
@@
 $ 
-s=s_{10} \wedge s_{1{(n_1+1)}}\!=s',
+s=s_{10} \wedge s_{1{(n_1+1)}}\!=s',\quad
 \displaystyle{\set{\gamma_1}= \mybigdotcup_{i=0}^{n_1} \vis{\set{\beta_{1 i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1 j} } }} \\
-\Pred_1\!=\!\bigwedge_{i=0}^{n_1}(\Pred_{1i} \subst{\bigotimes_{j=i-1}^{0}\Post_{i j}} ), \Post_1= \bigotimes_{i=n_1}^{0} \subst{\Post_{1i}} 
+\Pred_1\!=\!\bigwedge_{i=0}^{n_1}(\Pred_{1i} \subst{\bigotimes_{j=i-1}^{0}\Post_{i j}} ), \quad \Post_1= \bigotimes_{i=n_1}^{0} \subst{\Post_{1i}} 
 $
@@
 $ 
-s''=s_{30} \wedge s_{3{(m_1+1)}}\!=s''',
+s''=s_{30} \wedge s_{3{(m_1+1)}}\!=s''',\quad
 \displaystyle{\set{\gamma_3}= \mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{3 i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{3 j} } }} \\
-\Pred_3\!=\!\bigwedge_{i=0}^{m_1}(\Pred_{3i} \subst{\bigotimes_{j=i-1}^{0}\Post_{3 j}} ), \Post_3= \bigotimes_{i=m_1}^{0} \subst{\Post_{3i}} 
+\Pred_3\!=\!\bigwedge_{i=0}^{m_1}(\Pred_{3i} \subst{\bigotimes_{j=i-1}^{0}\Post_{3 j}} ),\quad \Post_3= \bigotimes_{i=m_1}^{0} \subst{\Post_{3i}} 
 $
@@
  and  \\
-$\Pred_{s,t} \land \Pred_{OT}\\
-\displaystyle{\implies\!\!\! \bigvee_{x\in X}
+$\Pred_{s,t} \land \Pred_{OT}\implies\\
+\displaystyle{\bigvee_{x\in X}
    \left( \forall j\in J_x.\gamma_j\!=\!\gamma_{jx}\!\land\! \Pred_{OT_x}
@@
  such that  $\forall a, J_{a}=\{j\in J_1'|\beta_{1j}\neq\tau\},   (s_{11},u_a|\Pred_{s_{11},u_a})\in \mathcal{R}$ and \\
- $\Pred_{s,t} \land \Pred_1\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
+ $\Pred_{s,t} \land \Pred_1\implies\\
+ \displaystyle{\bigvee_{a\in A}}
   \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}\!=\!\gamma_{ja} \!\land\! \Pred_{OT_a}\!
@@
 (s_{21},v_{b}|\Pred_{s_{21},v_{b}})\in \mathcal{R}$; \\
- $\Pred_{s_{11},u_a} \land \Pred_2\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{b\in B}}
+ $\Pred_{s_{11},u_a} \land \Pred_2\implies\\
+\displaystyle{\bigvee_{b\in B}}
  \!\!  \left( \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}\land \Pred_{OT_{b}}\!\land \alpha'\!=\!\alpha_{2 b}\! \land\!  
@@
 (s_{31},w_{c}|\Pred_{s_{31},w_{c}})\in \mathcal{R}$ and \\
- $\Pred_{s_{21},v_{b}} \land \Pred_3\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{c\in C}}
+ $\Pred_{s_{21},v_{b}} \land \Pred_3\implies\\
+\displaystyle{\bigvee_{c\in C}}
    \!\left( \forall j\in J_{c}. \vis{\beta_{3j}}\!=\!\gamma_{jc} \! \land\! \Pred_{OT_{c}}\!
@@
 We now need to prove that the following statement holds:\\
-$\Pred_{s,t} \land \Pred\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} 
+$\Pred_{s,t} \land \Pred\implies\\
+ \displaystyle{\bigvee_{x\in X}} 
   ( \forall j\in J. \gamma_j'=\gamma_{j}  \land \Pred
@@
 Moreover, we have the following  statement:\\
-$\Pred_{s,t} \land \Pred_1\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
+$\Pred_{s,t} \land \Pred_1\implies\\
+ \displaystyle{\bigvee_{a\in A}}
  \! \! \left( \forall j\in J_a. \vis{\beta_{1j}}=\gamma_{ja}  \land \Pred_{OT_a}
@@
 With the conjunction of the predicate $\Pred_2\subst{\Post_1}$ on both sides of the implication, we get:\\  
-$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
- \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
-  \!\! ( \forall j\in J_a. \vis{\beta_{1j}}=\gamma_{ja}  \land \Pred_{OT_a} \land
-     \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}) \wedge\\ \Pred_2\subst{\Post_1\uplus\Post_{OT_a}}  \\
+$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies \\
+ \displaystyle{\bigvee_{a\in A}}
+  \!\! ( \forall j\in J_a. \vis{\beta_{1j}}=\gamma_{ja}\!  \land\! \Pred_{OT_a}\! \land\!
+     \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}) \wedge \Pred_2\subst{\Post_1\uplus\Post_{OT_a}}  \\
 $
@@
 Hence a little rewriting gives:\\
-$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
- \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
+$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies\\
+\displaystyle{\bigvee_{a\in A}}
 \!\!   \left(\forall j\in J_a. \vis{\beta_{1j}}\!=\!\gamma_{ja}\land \Pred_{OT_a}
@@
 By replacing the inner predicate $(\Pred_{s_{11},u_a}\wedge\Pred_2)$ by the conclusion of the  statement given in case 2,  the formula becomes: \\
-$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
- \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
+$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies\\
+\displaystyle{\bigvee_{a\in A}}
    \!\!(\forall j\in J_a. \vis{\beta_{1j}}\!\!=\!\gamma_{ja}  \land \Pred_{OT_a}
       \land (\displaystyle{\bigvee_{b\in B}}(
-    \forall j\in J_{b}.
-\vis{\beta_{2j}}\!=\!\gamma_{jb}  \land \Pred_{OT_{b}}\land \\~\qquad\qquad\alpha'\!=\!\alpha_{2 b}\!
-\land \Pred_{s_{21},v_{b}}\subst{\Post_2\uplus\Post_{OT_{b}}})\subst{\Post_1\uplus\Post_{OT_a}})$\\
+    \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}  \land \Pred_{OT_{b}}\!\land 
+    \alpha'\!=\!\alpha_{2 b} \land\\ \Pred_{s_{21},v_{b}}\subst{\Post_2\uplus\Post_{OT_{b}}})\subst{\Post_1\uplus\Post_{OT_a}})$\\
 This can be rewritten into:\\
-$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}} 
+$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1} \implies\\
+\displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}} 
 (\forall j\in J_a.
 \vis{\beta_{1j}}\!\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-(\vis{\beta_{2j}}\!=\!\gamma_{jb})\subst{\Post_1\uplus\Post_{OT_a}}   \land\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_1\uplus\Post_{OT_a}} \land  (\alpha'\!=\!\alpha_{2 b}) \subst{\Post_1\uplus\Post_{OT_a}} \land \\ \Pred_{s_{21},v_{b}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
+(\vis{\beta_{2j}}\!=\!\gamma_{jb})\subst{\Post_1\uplus\Post_{OT_a}}   \land\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_1\uplus\Post_{OT_a}} \land  (\alpha'\!=\!\alpha_{2 b}) \subst{\Post_1\uplus\Post_{OT_a}} \land\\ \Pred_{s_{21},v_{b}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
 Since $Post_1$  does not act on $\gamma_{jb}$, nor on $ \Pred_{OT_{b}}$ and $  \alpha_{2}$.
 As well $\Post_{OT_a}$  does not act on $\alpha'$, nor on  $\beta_{2j}$ the formula can be simplified as follows:\\
-$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}} 
+$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies\\
+\displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}} 
 (\forall j\in J_a.
 \vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-\vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jb} \subst{\Post_{OT_a}}  \land\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_{OT_a}} \land \alpha'\subst{\Post_1}=\alpha_{2 b} \subst{\Post_{OT_a}} \land \Pred_{s_{21},v_b}\\\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
+\vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jb} \subst{\Post_{OT_a}}  \land\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_{OT_a}} \land \alpha'\subst{\Post_1}=\alpha_{2 b} \subst{\Post_{OT_a}} \land\\ \Pred_{s_{21},v_b}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
 Finally, the conjunction with the term $\Pred_3\subst{\Post_2\shortotimes\Post_1}$ of the both sides of the implication and rewriting, we get:\\
-$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}} \displaystyle{\bigvee_{b\in B}} 
+$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\implies \\
+\displaystyle{\bigvee_{a\in A}} \displaystyle{\bigvee_{b\in B}} 
 (\forall j\in J_a.\vis{\beta^1_j}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
@@
 by the conclusion of the  implication given in case 3, we get:\\
-$\Pred_{s,t} \land \underbrace{\Pred_1\land \Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}}_{\Pred_{OT}}\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}}\, \displaystyle{\bigvee_{c\in C}} 
+$\Pred_{s,t} \land \underbrace{\Pred_1\land \Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}}_{\Pred_{OT}}\implies\\
+ \displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}}\, \displaystyle{\bigvee_{c\in C}} 
 (\forall\! j\in\! J_a.\vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \!\in\! J_{b}.\vis{\beta_{2j}\subst{\Post_{OT_a}}}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}  \land 
@@
 $\forall j\in J_a\uplus J_b\uplus J_c.
-\vis{\beta_{1j}}\dotcup \vis{\beta_{2j}\subst{\Post_{OT_a}}}\dotcup \vis{\beta_{3j} \subst{\Post_2\,\shortotimes\,\Post_1}}=\gamma_{j a} \dotcup \gamma_{jb} \subst{\Post_{OT_a}}  \dotcup \gamma_{jc} \subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}
+\vis{\beta_{1j}}\dotcup \vis{\beta_{2j}\subst{\Post_{OT_a}}}\dotcup \vis{\beta_{3j} \subst{\Post_2\,\shortotimes\,\Post_1}}= \gamma_{j a} \dotcup \gamma_{jb} \subst{\Post_{OT_a}}  \dotcup \gamma_{jc} \subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}
 $ \\
 We have  $s_{31}=s'$, so can rewrite the formula:\\
-$\Pred_{s,t} \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}} \displaystyle{\bigvee_{b\in B}} \displaystyle{\bigvee_{c\in C}} 
+$\Pred_{s,t} \land \Pred_{OT}\implies\\
+\displaystyle{\bigvee_{a\in A}} \displaystyle{\bigvee_{b\in B}} \displaystyle{\bigvee_{c\in C}} 
 (\forall j\in J.\gamma_j'=\gamma_j \land  \Pred \land \alpha=\alpha''  \land \Pred_{s',w_{c}}\subst{\Post_{OT}\uplus\Post\,}$\\
@@
 This re-indexing allows us to conclude:\\
-$\Pred_{s,t} \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} 
+$\Pred_{s,t} \land \Pred_{OT}\implies\\\
+ \displaystyle{\bigvee_{x\in X}} 
 (\forall j\in J.\gamma_j'=\gamma_j \land  \Pred \land \alpha=\alpha''  \land \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,}$\\
@@
 \gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!
-\Post_{1j}}}\dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }}
+\Post_{1j}}}\dotcup\  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}}} \dotcup \\ ~\quad\,\qquad \displaystyle{\mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }}
 \\
@@
 \begin{enumerate}
-\item For each open transition  $\symb{OT}_p$ in the form ($\set{\beta_{1p}}=\beta_{1pj}^{j\in J_{1p}}$): 
-$P[Q]_{j_0}\!\models		
+\item For each open transition  $\symb{OT}_p$ in the form ($\set{\beta_{1p}}=\beta_{1pj}^{j\in J_{1p}}$):\\ 
+\[P[Q]_{j_0}\!\models		
 \openrule
@@
        {\beta_{1pj}^{j\in J_{1p}}},\Pred_{1p},\Post_{1p}   }
-         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$ \\
+         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}\] 
 If $Q$ moves then we obtain by Lemma \ref{lem-decompose}:\\
-$P\models{\openrule
+\begin{small}$P\models{\openrule
 			{
 				(\beta_{1pj})^{j\in (J_{1p}\setminus \Holes(Q)) \cup \{j_0\}}, 
-				{\Pred'_{1p}},  
-				{\Post'_{1p}}}
+				{\Pred\,'_{1p}},  
+				{\Post\,'_{1p}}}
 			{\ostate{s_{p l}^{l\in L\setminus L_Q}} \OTarrow {\tau}
@@
 		}%\]
-	\,\text{~~and~~} 
+	\text{~~and~~} 
 		Q\models{\openrule
 			{
-				(\beta_{1pj})^{j\in J_{1p}\cap\Holes(Q)}, {\Pred''_{1p}},  
-				{\Post''_{1p}}}
+				(\beta_{1pj})^{j\in J_{1p}\cap\Holes(Q)}, {\Pred\,''_{1p}},  
+				{\Post\,''_{1p}}}
 				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{1p}}
@@
 $
-such that  $\Pred_{1p} \iff {\Pred'_{1p}}
-		\land {\Pred''_{1p}}\land \alpha_{1p}=\beta_{1pj_0}$, $\Post_{1p}={\Post'_{1p}}\uplus 
-		{\Post''_{1p}}$ where ${{\Post''_{1p}}}$ is the restriction of $\Post_{1p}$ over variables of $\Leaves(Q)$.\\
+\end{small}
+such that  \\
+$\Pred_{1p} \!\!\iff\!\!
+{\Pred\,'_{1p}}\land {\Pred\,''_{1p}}\land\alpha_{1p}\!=\!\beta_{1pj_0}$, $\Post_{1p}\!=\!{\Post\,'_{1p}}\uplus{\Post\,''_{1p}}$  where ${{\Post\,''_{1p}}}$ is the restriction of $\Post_{1p}$ over variables of $\Leaves(Q)$.\\
 Else $Q$ does not move and we have: \\
+\begin{small}
 $P\models{\openrule
@@
 				(\beta_{1pj})^{j\in (J_{1p}\setminus \Holes(Q)) }, 
-				{\Pred'_{1p}},  
-				{\Post'_{1p}}}
+				{\Pred\,'_{1p}},  
+				{\Post\,'_{1p}}}
 			{\ostate{(s_{p l})^{l\in L\setminus L_Q}} \OTarrow {\tau}
@@
 		}$~~and~~ $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}} $
-
+\end{small}
 \item Similarly, we have similar open transitions on states $u_{pl}$ (for the final $\tau$ transitions).
 
-\item Finally, for the open transition in the form ($\set{\beta_{2}}=\beta_{2j}^{j\in J_2}$): $P[Q]_{j_0}	\models \openrule
+\item Finally, for the open transition in the form ($\set{\beta_{2}}=\beta_{2j}^{j\in J_2}$):\\ 
+\[P[Q]_{j_0}	\models \openrule
          {
            \beta_{2j}^{j\in J_2},\Pred_2,\Post_2 }
-         {\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'} \ostate{(t'_l)^{l\in L_Q}}}$\\
+         {\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'} \ostate{(t'_l)^{l\in L_Q}}}\]
 If $Q$ moves then we  obtain by Lemma \ref{lem-decompose}:\\
-$
+\begin{small}$
 		P\models{\openrule
@@
 				(\beta_{2j})^{j\in (J_2\setminus \Holes(Q)) \cup \{j_0\}}, 
-				{\Pred'_2},  
-				{\Post'_2}}
+				{\Pred\,'_2},  
+				{\Post\,'_2}}
 			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha'}
@@
 			{
-				(\beta_{2j})^{j\in J_2\cap\Holes(Q)}, {\Pred''_2},  
-				{\Post''_2}}
+				(\beta_{2j})^{j\in J_2\cap\Holes(Q)}, {\Pred\,''_2},  
+				{\Post\,''_2}}
 			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_2}
@@
 		}%\]
-$\\
-such that  $\Pred_2 \iff {\Pred'_2}
-		\land {\Pred''_2}\land \alpha_2=\beta_{2j_0}$, $\Post_2={\Post'_2}\uplus 
-		{\Post''_2}$ where ${\Post''_2}$ is the restriction of $\Post_2$ over variables of $\Leaves(Q)$.
+$
+\end{small}\\
+such that  $\Pred_2 \iff {\Pred\,'_2}
+		\land {\Pred\,''_2}\land \alpha_2=\beta_{2j_0}$, $\Post_2={\Post\,'_2}\uplus 
+		{\Post\,''_2}$ where ${\Post\,''_2}$ is the restriction of $\Post_2$ over variables of $\Leaves(Q)$.
 
 Else $Q$ does not move and we have \\
-$
-		P\models{\openrule
+$\begin{small} P\models{\openrule
 			{
 				(\beta_{2j})^{j\in (J_2\setminus \Holes(Q)) \cup \{j_0\}}, 
-				{\Pred'_2},  
-				{\Post'_2}}
+				{\Pred\,'_2},  
+				{\Post\,'_2}}
 			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha'}
@@
 	\,\text{~~and~~} \ostate{t_l^{l\in L_Q}} = 
-				\ostate{(t_l')^{\,l\in L_Q}}$
+				\ostate{(t_l')^{\,l\in L_Q}} \end{small}$
 
@@
 and \\%$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\}$,\\
-${(\gamma_j')}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}} \dotcup\\
+${(\gamma_j')}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}}} \dotcup\\
 ~~\qquad \qquad\qquad\qquad\qquad \mybigdotcup_{i=0}^{m_2}
-\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}} }\\
-\Pred\,'=\bigwedge_{i=0}^{m_1}\Pred'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}\land\Pred'_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}\land\\ 
-~\qquad\qquad\bigwedge_{i=0}^{m_2}\Pred'_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}\\
-\Post'=\bigotimes_{j=m_2}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}$
+\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}} }\\
+\Pred\,'=\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}\land\\ 
+~\qquad\qquad\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}\\
+\Post'=\bigotimes_{j=m_2}^{0}\!\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}$
 
@@
 
-We denote the following predicate (we will need it for reasoning on the global predicate and will reason on it along the proof):
-\[\begin{array}{l}\displaystyle{
-\Pred_\beta=\bigwedge_{p=0}^{m_1}(\beta_{1pj_0}=\alpha_{1p})\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}} \wedge (\beta_{2j_0}=\alpha_2)\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}}\\\quad
+We denote the following predicate (we will need it for reasoning on the global predicate and will reason on it along the proof):\\
+$\begin{array}{l}\displaystyle{
+\Pred_\beta=\bigwedge_{p=0}^{m_1}(\beta_{1pj_0}=\alpha_{1p})\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}} \wedge (\beta_{2j_0}=\alpha_2)\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}} \wedge \\\qquad\qquad
 \displaystyle{
-\wedge\bigwedge_{p=0}^{m_2}(\beta_{3pj_0}=\alpha_{3p})
+\bigwedge_{p=0}^{m_2}(\beta_{3pj_0}=\alpha_{3p})
 \subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}}
-\end{array}\]
+\end{array}$
 
@@
 So we have: \\
+\begin{small}
 $\forall p\! \in\! [0..n_1] Q\models{\openrule
 			{
-				(\beta_{1pj}')^{j\in J\cap\Holes(Q)}, {{\Pred''_{1p}}},  
-				{{\Post''_{1p}}}}
+				(\beta_{1pj}')^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{1p}}},  
+				{{\Post\,''_{1p}}}}
 				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{1p}}
@@
 				}%\]
-,$  \\
+,$  
 $ Q\models{\openrule
 			{
-				(\beta'_{2 j})^{j\in J\cap\Holes(Q)}, {\Pred''_2},  
-				{\Post''_2}}
+				(\beta'_{2 j})^{j\in J\cap\Holes(Q)}, {\Pred\,''_2},  
+				{\Post\,''_2}}
 			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_2}
@@
 			{
-				(\beta'_{3pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_{3p}}},  
-				{{\Post''_{3p}}}}
+				(\beta'_{3pj})^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{3p}}},  
+				{{\Post\,''_{3p}}}}
 				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha_{3p}}
@@
 				}%\]
-$\\ 
+$
+\end{small}
+\\ 
 such that $n_1 \leq m_1$ and $n_2 \leq m_2$.\\
@@
 			{
-				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred''_p}},  
-				{{\Post''_p}}}
+				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_p}},  
+				{{\Post\,''_p}}}
 				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
@@
 (\alpha_{1p}=\beta_{1pj_0})\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}&\iff
-\alpha_{1p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post''_{1j}}
-= \beta_{1 p j_0}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post'_{1j}} \\
-&\iff\alpha_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post''_{j}}= \beta_{1 p j_0}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post'_{1j}} 
+\alpha_{1p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,''_{1j}}
+= \beta_{1 p j_0}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,'_{1j}} \\
+&\iff\alpha_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post\,''_{j}}= \beta_{1 p j_0}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,'_{1j}} 
 \end{split}
@@
 \Pred_\beta \iff \gamma_{j_0}=
-\vis{[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post''_{j}}|p\in[0..n_1+n_2+2]]}
+\vis{[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,''_{j}}|p\in[0..n_1+n_2+2]]}
 \end{equation}
@@
 We obtain $n+1$ subsequences  made of the following OTs, for all $k\in [0..n]$ :\\
+\begin{small}
 $\forall p\! \in\! [n'_{k}..(n_k\!-\!1)] Q\models{\openrule
 			{
-				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred''_{p}}},  
-				{{\Post''_{p}}}}
+				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{p}}},  
+				{{\Post\,''_{p}}}}
 				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
@@
 				}%\]
-,$ \\
-$Q\models{\openrule
-			{
-				\beta_{n_k j}^{j\in J\cap\Holes(Q)}, {{\Pred''_{n_k}}},  
-				{{\Post''_{n_k}}}}
+,\quad
+Q\models{\openrule
+			{
+				\beta_{n_k j}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{n_k}}},  
+				{{\Post\,''_{n_k}}}}
 				{\ostate{v_{n_kl}^{l\in L_Q}} \OTarrow {\alpha_{{n_k}}}
@@
 $
+\end{small}
 and\\
+\begin{small}
 $\forall p \in [(n_k\!+\!1)..(n'_{k+1}\!-\!1)]\,\, Q\models{\openrule
 			{
-				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred''_{p}}},  
-				{{\Post''_{p}}}}
+				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{p}}},  
+				{{\Post\,''_{p}}}}
 				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
@@
 				}%\]
-$\\ 
+$
+\end{small}
+\\ 
 Thereafter, by Lemma \ref{lem-rel-OT-WOT} we can deduce the following weak open transition:
@@
 \end{mathpar}
-$\alpha_k'=\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post''_{j}}}$\\
+$\alpha_k'=\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}}$\\
 $\forall l \in L_Q. v_{kl}=v_{(n'_{k})l} \wedge v_{kl}'=v_{(n'_k)l}$\\
-$\displaystyle{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=\displaystyle{\mybigdotcup_{i=n'_{k}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k}}\!\!\!\Post''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post''_{l}}}} \dotcup\\
+$\displaystyle{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=\displaystyle{\mybigdotcup_{i=n'_{k}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}} \dotcup\\
 ~~\qquad \qquad\qquad\mybigdotcup_{i=n_k+1}^{n'_{k+1}-1}
-\vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}} \subst{\bigotimes_{l=i-1}^{n_k\!+\!1}\!\Post''_{l}\shortotimes\Post''_{n_k}\shortotimes\!\!\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post''_{l}} }\\
-%
-\Pred_k=\bigwedge_{i=n'_{k}}^{n_k\!-\!1}\!\!\Pred''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\Post''_{j}}\land\Pred''_{n_k} \subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post''_{j}}\land\\ 
-~\qquad\quad\bigwedge_{i=n_k+1}^{n'_{k+1}-1}\!\!\!\Pred''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\!\Post''_{j}\shortotimes\Post''_{n_k}\shortotimes\!\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post''_{j}}
+\vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}} \subst{\bigotimes_{l=i-1}^{n_k\!+\!1}\!\Post\,''_{l}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}} }\\
+%
+\Pred_k=\bigwedge_{i=n'_{k}}^{n_k\!-\!1}\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\Pred\,''_{n_k} \subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\\ 
+~\qquad\quad\bigwedge_{i=n_k+1}^{n'_{k+1}-1}\!\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\!\Post\,''_{j}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{j}}
 \\
-\Post_k= \bigotimes_{j=n'_{k+1}-1}^{n'_{k}}\!\!\Post''_{j}$\\
-
-Note that for all $k\in[0..n-1]$, $v_{kl}'=v_{(k+1)l}$,  $v_{0l}=s_{0l}=s_l$, and $v'_{nl}=v_{(n_1+n_2+3) l}=u_{(n_2+1) l} = s'_l$.
-
-By definition of $\Post_k$, we have $\displaystyle{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j} = \bigotimes_{j=k-1}^{0}\!\!\Post_{j}}$.
+\Post_k= \bigotimes_{j=n'_{k+1}-1}^{n'_{k}}\!\!\Post\,''_{j}$\\
+
+\noindent Note that for all $k\in[0..n-1]$, $v_{kl}'=v_{(k+1)l}$,  $v_{0l}=s_{0l}=s_l$, and $v'_{nl}=v_{(n_1+n_2+3) l}=u_{(n_2+1) l} = s'_l$.
+
+\noindent By definition of $\Post_k$, we have $\displaystyle{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post\,''_{j} = \bigotimes_{j=k-1}^{0}\!\!\Post_{j}}$.
 %In this case, the number of weak open transitions
@@
 Consequently,  we have:
-\[\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{0}\!\!\Post''_{j}}} =
-\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post''_{j}\otimes\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j}}} = \alpha_k'\displaystyle{\subst{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post''_{j}}} =
-\alpha_k'\displaystyle{\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}}\]
+\[\alpha_{n_k}\displaystyle{\subst{\!\bigotimes_{j=n_k-1}^{0}\!\!\!\Post\,''_{j}}} =
+\alpha_{n_k}\displaystyle{\subst{\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post''_{j}\otimes\!\!\!\bigotimes_{j=n'_{k}-1}^{0}\!\!\!\Post\,''_{j}}} = \alpha_k'\displaystyle{\subst{\!\bigotimes_{j=n'_{k}-1}^{0}\!\!\!\Post\,''_{j}}} =
+\alpha_k'\displaystyle{\subst{\!\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}}\]
 With~\ref{eqproofbeta}, we now have (the actions $\alpha'_p$ correspond to the observable actions, $\alpha_k$): 
@@
 We can assert a similar equality on postconditions, i.e.
-between $\Post''_p$ and $\Post''_{1k}$, $\Post''_{2}$, $\Post''_{3k}$ where $\Post''_{1p}$ is the restriction of $\Post_{1p}$ over variables of $\Leaves(Q)$ (see initial decomposition, case 1, 2, and 3 above).
+between $\Post\,''_p$ and $\Post\,''_{1k}$, $\Post\,''_{2}$, $\Post\,''_{3k}$ where $\Post\,''_{1p}$ is the restriction of $\Post_{1p}$ over variables of $\Leaves(Q)$ (see initial decomposition, case 1, 2, and 3 above).
 Overall, we have
@@
 $\Pred = \displaystyle{\Pred\,'
-		\land \!\!\bigwedge_{p=0}^n((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} )}$
-
+		\land \!\!\bigwedge_{p=0}^n((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} )}$\\
 Indeed,
-{\scriptsize \begin{equation*}
+\begin{small}
+\begin{equation*}
 \begin{split}
@@
 \bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
-&\iff\bigwedge_{i=0}^{m_1}\left(\Pred'_{1i}
-		\land {\Pred''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}\right)\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}} \\
-&\qquad\land\left(\Pred'_{2}
-		\land {\Pred''_{2}}\land \alpha_{2}=\beta_{2j_0}\right)\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
-&\qquad\land\bigwedge_{i=0}^{m_2} \left(\Pred'_{3i}
-		\land {\Pred''_{3i}}\land \alpha_{3i}=\beta_{3ij_0}\right) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
-&\iff\bigwedge_{i=0}^{m_1}\left((\Pred'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}})
-		\land ({\Pred''_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post''_{1j}})\land (\alpha_{1i}=\beta_{1ij_0})\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\right) \\
-&\qquad\land \left(\Pred'_{2}\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}
-		\land {\Pred''_{2}} \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \land (\alpha_{2}=\beta_{2j_0})\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \right) \\
-&\qquad\land\bigwedge_{i=0}^{m_2} \Bigg(\Pred'_{3i} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} 
-		\land {\Pred''_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}  \\
+&\iff\bigwedge_{i=0}^{m_1}\left(\Pred\,'_{1i}
+		\land {\Pred\,''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}\right)\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}} \\
+&\qquad\land\left(\Pred\,'_{2}
+		\land {\Pred\,''_{2}}\land \alpha_{2}=\beta_{2j_0}\right)\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
+&\qquad\land\bigwedge_{i=0}^{m_2} \left(\Pred\,'_{3i}
+		\land {\Pred\,''_{3i}}\land \alpha_{3i}=\beta_{3ij_0}\right) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
+&\iff\bigwedge_{i=0}^{m_1}\left((\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{1j}})
+		\land ({\Pred\,''_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,''_{1j}})\land (\alpha_{1i}=\beta_{1ij_0})\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\right) \\
+&\qquad\land \left(\Pred\,'_{2}\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}
+		\land {\Pred\,''_{2}} \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \land (\alpha_{2}=\beta_{2j_0})\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \right) \\
+&\qquad\land\bigwedge_{i=0}^{m_2} \Bigg(\Pred\,'_{3i} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} 
+		\land {\Pred\,''_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}  \\
 		 & \qquad \land (\alpha_{3i}=\beta_{3ij_0}) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\Bigg)  \\
-&\iff \Pred'\land\bigwedge_{k=0}^n\Pred_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}\land\Pred_\beta
-\\&\iff \Pred'\land\bigwedge_{k=0}^n\Pred_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}\land
+&\iff \Pred\,'\land\bigwedge_{k=0}^n\Pred_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}\land\Pred_\beta
+\\&\iff \Pred\,'\land\bigwedge_{k=0}^n\Pred_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}\land
 (\gamma_{j_0}=[\alpha'_{i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{j}}|i\in[0..n]])
 \end{split}\end{equation*}
-}
+\end{small}
 which is exactly what is needed.\\
@@
 \Post&=\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}\\
-&=\bigotimes_{j=m_2}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j} \uplus \bigotimes_{j=m_2}^{0}\!\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}\\
-&=\Post' \uplus \bigotimes_{j=n'_{n+1}-1}^{0}\!\!\Post''_{j}
+&=\bigotimes_{j=m_2}^{0}\!\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j} \uplus \bigotimes_{j=m_2}^{0}\!\!\Post\,''_{3j}\shortotimes\Post\,''_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,''_{1j}\\
+&=\Post\,' \uplus \bigotimes_{j=n'_{n+1}-1}^{0}\!\!\Post\,''_{j}
 \end{split}
@@
 such that\\ 
-{\footnotesize $\alpha_Q=\alpha'_Q\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$\\
+$\alpha_Q=\alpha'_Q\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$\\
 $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\
+\begin{small}
 $\displaystyle{
@@
 $
-}
+\end{small}
 \begin{enumerate}
@@
 and $\alpha=\alpha'$  because $\Post_{1j}$ acts on variables of $Q$ and $\alpha$ contains only variables of $P$.\\
-{\footnotesize $\displaystyle{
+$\displaystyle{
 \set{\gamma_c}=\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{i=h-1}^{0}\!\!
@@
 $~~\hspace{0.6em}=\set{\gamma}\uplus\vis{\beta_j^{\in J\setminus \{j_0\}}} \quad$  because $\Post_{1j}$  does not act on variables of $\beta_j$.  \\
+\begin{small}
 $\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_{1i}}\land
@@
 $\\
-$\Post_c=\displaystyle{(\bigotimes_{i=k'}^{0}{\Post_{3i}})\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}$
-}
-Note that we have $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\
+$\Post_c=\displaystyle{(\bigotimes_{i=k'}^{0}{\Post_{3i}})\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}$\\
+\end{small}
+\noindent Note that we have $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\
 
@@
 By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
-\begin{mathpar}
-\forall p\!\in\![0..m_1].P\models\openrule
+%\begin{mathpar}
+\begin{small}
+$\forall p\!\in\![0..m_1].P\models\openrule
     {{\beta_{1pj}^{j\in J_{1p}}},\Pred_{1p},\Post_{1p}   }
-         {\ostate{{(s_{1pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s_{1(p+1)i})}^{i\in L}}}  \\ 
+         {\ostate{{(s_{1pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s_{1(p+1)i})}^{i\in L}}},  \quad
 P\models\openrule
          {\beta_{2j}^{j\in J_2},\Pred_2,\Post_2 }
-         {\ostate{({s_{20i}})^{i\in L}} \OTarrow {\alpha'} \ostate{({s_{21i}})^{i\in L}}}
+         {\ostate{({s_{20i}})^{i\in L}} \OTarrow {\alpha'} \ostate{({s_{21i}})^{i\in L}}} $ 
 \\
-\forall p \in [0..m_2].P\models\openrule
+and  $\forall p \in [0..m_2].P\models\openrule
          {
            \beta_{3pj}^{j\in J_{3p}},\Pred_{3p}, \Post_{3p}}
-         { \ostate{(s_{3pi})^{i\in L}} \OTarrow {\tau} \ostate{(s_{3(p+1)i})^{i\in L}}}
-\end{mathpar}
-where for all $i\in L$:\\
+         { \ostate{(s_{3pi})^{i\in L}} \OTarrow {\tau} \ostate{(s_{3(p+1)i})^{i\in L}}}$
+\end{small}
+~~\\
+%\end{mathpar}
+\noindent where for all $i\in L$:\\
 $s_i=s_{10 i} \wedge s_{1(m_1+1) i}=s_{20i} \wedge  s_{21i}= s_{30 i} \wedge s_{3(m_2+1) i}=s'_i$\\
@@
 %\begin{multline*}
-$\gamma_j^{j\in J}=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \dotcup \, \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}} \\
-~~\qquad~\dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{3p}} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}$\\
+$\gamma_j^{j\in J}=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \dotcup \, \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}}\, \dotcup\\
+~\qquad\quad \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{3p}} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}$\\
 %\end{multline*}
@@
 $~~\qquad\quad\displaystyle{\bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}}$\\
-$\Post=\displaystyle{\bigotimes_{p=m_2}^{0}\Post_{3p}\otimes\Post_2\otimes\bigotimes_{j=m_1}^{0}\Post_{1j}}$
+$\Post=\displaystyle{\bigotimes_{p=m_2}^{0}\Post_{3p}\otimes\Post_2\otimes\bigotimes_{j=m_1}^{0}\Post_{1j}}$\\
 %\end{multline*}
@@
 $\gamma_{j_0}=[\beta_0..\beta_n]\\
-~~\quad =\displaystyle{\mybigdotcup_{\substack{i=0\\j_0\in J_{1i}}}^{m_1} \vis{{\beta_{1ij_0}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \dotcup \vis{{\beta_{2j_0}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}} \\
-~~\quad~\displaystyle{ \dotcup \mybigdotcup_{\substack{i=0\\j_0\in J_{3i}}}^{m_2} \vis{{\beta_{3ij_0}} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}}$\\
+~~\quad =\displaystyle{\mybigdotcup_{\substack{i=0\\j_0\in J_{1i}}}^{m_1} \vis{{\beta_{1ij_0}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \dotcup \vis{{\beta_{2j_0}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}}\, \dotcup \\
+~\qquad\quad\displaystyle{ \mybigdotcup_{\substack{i=0\\j_0\in J_{3i}}}^{m_2} \vis{{\beta_{3ij_0}} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}}$\\
 
@@
 \set{\gamma'}=
- \mybigdotcup_{i=0}^{m_1}\set{\gamma'_{1i}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{1k}}\dotcup
- \set{\gamma'_{2}}\subst{\bigotimes_{k=m_1}^{0}\Post\,'_{1k}}\dotcup
- \mybigdotcup_{i=0}^{m_2}\set{\gamma'_{3i}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}
+ \mybigdotcup_{i=0}^{m_1}\set{\gamma'_{1i}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{1k}}\,\dotcup\,
+\set{\gamma'_{2}}\subst{\bigotimes_{k=m_1}^{0}\Post\,'_{1k}}\,\dotcup}\\
+\displaystyle{~\qquad \mybigdotcup_{i=0}^{m_2}\set{\gamma'_{3i}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}
 }
@@
 \Pred\,''=\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\ 
-~\qquad\quad\Big(\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_2}^{0}\Post\,'_{1j}}\Big)\\
+~\qquad\qquad\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_2}^{0}\Post\,'_{1j}}\\
 \Post\,''=\bigotimes_{j=m_2}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}
@@
 \begin{align*}
-\alpha''&=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}\\
+\alpha''&=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}}\\
 & = \alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}}&\text{$\alpha'$ only contains variables of $P$ untouched by $\Post_i$}\\
@@
 For $\set{\gamma'}$ we distinguish elements in the holes of $P$ and of $Q$.
-First suppose $j\in J\setminus\{j_0\}$ we have $\gamma'_j=\gamma_j$ because $\Post'_{ij}$ has no effect on variables of $P$ and on $\beta_{1pj}$, consequently
-\begin{multline*}
-\gamma'_j=\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \dotcup  \vis{{\beta_{2j}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}} \\
-\dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}
-\end{multline*}
+First suppose $j\in J\setminus\{j_0\}$ we have $\gamma'_j=\gamma_j$ because $\Post'_{ij}$ has no effect on variables of $P$ and on $\beta_{1pj}$, consequently\\
+
+$\displaystyle{\gamma'_j=\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \dotcup  \vis{{\beta_{2j}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}\, \dotcup}\\
+~\qquad\qquad \displaystyle{\mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}}
+$
+
 Now, when $j\in J_t$ for some $t$,  $\gamma'_j$ is the concatenation of elements of $\gamma'_{1ij}$, $\gamma'_{2 j}$, $\gamma'_{3ij}$  that are not empty.
@@
 $\Post_{ik}$ has no effect on $\gamma_{tj}$ but  $\Post_{k}$ has \TODO{do we want to be more explicit in the explanation?
-giving the exact indices is cumbersome because Post'ij is either empty or postij for the same indices as gamma, this can also be related with the ni and n'i}:
-\begin{align*}
-\gamma'_j&=
+giving the exact indices is cumbersome because Post'ij is either empty or postij for the same indices as gamma, this can also be related with the ni and n'i}:\\
+
+$\displaystyle{\gamma'_j =
 \mybigdotcup_{i=0}^{m_1}{\gamma'_{1ij}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{1k}}\dotcup
- {\gamma'_{2 j}}\subst{\bigotimes_{k=m_1}^{0}\Post\,'_{1k}}\dotcup
- \mybigdotcup_{i=0}^{m_2}{\gamma'_{3ij}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}\\
-&=
-\mybigdotcup_{t=0}^{n} {\gamma_{tj}}\subst{\bigotimes_{k=t-1}^{0} \Post_{k} }   
-\end{align*}
-
-Concerning predicates, we also separate predicates on $P$ from predicates on $Q$, and from the equality on the action filling the hole:
-{\footnotesize \begin{equation*}
+ {\gamma'_{2 j}}\subst{\bigotimes_{k=m_1}^{0}\Post\,'_{1k}}\,\dotcup}$\\
+$~\qquad \qquad\displaystyle{ \mybigdotcup_{i=0}^{m_2}{\gamma'_{3ij}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}}$\\
+$~\qquad \quad\displaystyle{\mybigdotcup_{t=0}^{n} {\gamma_{tj}}\subst{\bigotimes_{k=t-1}^{0} \Post_{k}}}$
+
+Concerning predicates, we also separate predicates on $P$ from predicates on $Q$, and from the equality on the action filling the hole:\\
+\begin{small}
+$
+\displaystyle{\Pred\,''=\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land}$\\
+$~\qquad\qquad\displaystyle{\bigwedge_{i=0}^{m_3}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}}$\\
+$~\qquad\quad=\displaystyle{\big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land}$\\
+$~\qquad\qquad\,\displaystyle{\bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\big) \land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i \land}$\\
+%$~\qquad\qquad\,\displaystyle{\bigwedge_{i=0}^{m-1}(\beta_{1{n_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j={n_i}-1}^{0}\Post\,'_{1j}}\land(\beta_{2{j_0}}=\alpha_m) \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land}$\\
+%$~\qquad\qquad\,\displaystyle{\bigwedge_{i=m+1}^{n}(\beta_{3{n'_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j=n'_i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\Big)}$\\
+\end{small}
+%%%%%%% Je suis ici!!!!!
+
+\begin{small}
+\begin{equation*}
 \begin{split}
@@
 ~\quad\bigwedge_{i=0}^{m_3}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\Big)\\
-&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\&\qquad \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\Big)\\&\qquad
+&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\
+&\qquad \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\Big)\\&\qquad
 \land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i\\&\qquad
@@
 \end{equation*}
-}
+\end{small}
 
@@
 \]
-with $\bigvee_{x\in X}
-(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x} \implies \alpha_Q=\alpha_x$ that ensures that the open transitions can be recomposed when the OT fires.
+with $\displaystyle{\bigvee_{x\in X}
+(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x} \implies \alpha_Q=\alpha_x}$ that ensures that the open transitions can be recomposed when the OT fires.
 

### 2019-10-29 2016-Weak-FH-Bisim/WeakBisim.tex
text in sec 5.5

--- 2019-10-24 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
-\begin{definition}[Operational semantics of open pNets]
+\begin{definition}[Semantics of open pNets]
 	\label{def:operationalSemantics}
@@
 Indeed only the visible actions of the holes must be compared and they form a list of actions, but of length at most one.
-
 Weak FH-bisimilarity is an equivalence in the same way as strong FH-bisimilarity.
@@
 \subsection{Weak bisimulation for open pNets}
-\begin{definition}[Non-observability of silent actions for pNets]~\\
+
+Beforedefining a weak open automaton for the semantics of open pNets, it is necessary to state under which condition a pNet is unable to observe silent actions of its holes.
+In the setting of pNets this can simply be expressed as a condition on the synchronisation vectors.
+Precisely, the set of synchronisation vectors must contain vectors that let silent actions go through the pNet, i.e.
+synchronisation vectors where one hole does a $\tau$ transition, and the global visible action is a $\tau$.
+Additionally, no other synchronisation vector must be able to react on a silent action from a hole, i.e.
+if a synchronisation vector observes a $\tau$ from a hole it cannot synchronise it with another action nor emit an action that is not $\tau$.
+This is formalised as follows
+
+\begin{definition}[Non-observability of silent actions for pNets]\label{def:non-obspNet}~\\
 A pNet $\mylangle \pNet_i^{i\in I} , \Sort_j^{j\in J}, \set{\symb{SV}}\myrangle$
- \emph{cannot observe silent actions} if it verifies:\\ $\forall i\in I\uplus J.\, \SV{(i\mapsto \tau)}{\tau}{\True}\in \set{\symb{SV}}$ and $\forall SV_k\in \set{\symb{SV}}, \forall i,j\in I_k\uplus J_k.\,i\neq j \Rightarrow \alpha'_k\neq\tau$
+ \emph{cannot observe silent actions} if it verifies:\\ $\forall i\in I\uplus J.\, \SV{(i\mapsto \tau)}{\tau}{\True}\in \set{\symb{SV}}$ and 
+\begin{equation*}
+%\begin{split}
+\forall \left(\SV{{(\alpha_i)}^{i\in I'}} 
+{\alpha'} 
+{e_b}\in \set{\symb{SV}}\right), %&
+\forall i\in I'\cap J,\, \alpha_i=\tau \implies %\\
+%& 
+\alpha'=\tau ~\land~ %\\
+%&
+I'=\{i\}
+%\end{split}
+\end{equation*}
 \end{definition}
+
+With this definition, it is easy to check that the open automaton that gives the semantics of such an open pNet cannot observe silent actions in the sense of Definition~\ref{def:Non-ObsTau}:
 
@@
 %\TODO{question : we could merge prop 1 and def above, is it better?}
+
+Under this condition, it is safe to define the weak open automaton that provides a weak semantics to a given pNet.
+This is simply obtained by applying Definition~\ref{def:buildweakOT} to generate a weak open automaton from the open automaton that is the strong semantics of the open pNet, as provided by Definition~\ref{def:operationalSemantics}.
 

### 2019-10-29 2016-Weak-FH-Bisim/WeakBisim.tex
notation(cont.)

--- 2019-10-25 2016-Weak-FH-Bisim/WeakBisim.tex
@@
  	$\Pred_{s x}\subst{\Post_{OT}\uplus(\Post\,'\uplus \Post_{OT_x})}$, i.e.
- 	$\Pred_{s x}\subst{(\Post\,'\uplus 	\Post\,'')\uplus(\Post\,'\uplus \Post_{OT_x})}$. We 
+ 	$\Pred_{s, x}\subst{(\Post\,'\uplus 	\Post\,'')\uplus(\Post\,'\uplus \Post_{OT_x})}$. We 
  	can conclude by observing that	$\Pred_{s,x}$ does not use any variable of $P$ 
@@
 \land \alpha\!=\!\alpha_x}} 
-\land \Pred_{s x}\subst{\Post\,'\uplus\Post_{OT_x}}) 	
+\land \Pred_{s,x}\subst{\Post\,'\uplus\Post_{OT_x}}) 	
 $\end{small}
@@
 	change the validity of the formula (those variables are not used).
-	\item We need $\Pred_{s x}\subst{\Post_{OT}\uplus(\Post_{OT_x}\uplus \Post\,'')}$, i.e.:
+	\item We need $\Pred_{s, x}\subst{\Post_{OT}\uplus(\Post_{OT_x}\uplus \Post\,'')}$, i.e.,
 	$\Pred_{s,x}\subst{(\Post\,'\uplus \Post\,'')\uplus(\Post_{OT_x}\uplus \Post\,'')}$. We 
-	can conclude by observing that	$\Pred_{s x}$ does not use any variable of $Q$ 
+	can conclude by observing that	$\Pred_{s, x}$ does not use any variable of $Q$ 
 	and thus the substitution involving $\Post\,''$ has no effect.
@@
 \end{mathpar} 
-by rule (\WTDeux) we can directly conclude the implication: 
+by rule \WTDeux we can directly conclude the implication: 
  \begin{mathpar}
@@
            \set{\beta},\Pred,\Post}
-         {s \OTarrow {\alpha} s'} \in \mathcal{T} \implies 
+         {s \OTarrow {\alpha} s'} \in \mathcal{T} \Rightarrow 
 { \openrule
@@
 We consider the case $n'=n+1$ (because $m'=m+1$ is similar).
-We want to prove (1) $\implies$ (2) in the lemma, and in (1) we  focus on the case where there is a set of open transitions (this is the case: $s\neq s'$).
+We want to prove (1) $\Rightarrow$ (2) in the lemma, and in (1) we  focus on the case where there is a set of open transitions (this is the case: $s\neq s'$).
 In other words, we consider the sequence of ($n+m+2$) open transitions:
@@
 
-By recurrence hypothesis we suppose that the (1) $\implies$ (2) holds for $n$ and $m$ (compared to the line above, we remove the first $\tau$ transition). We have:\\
+By recurrence hypothesis we suppose that the (1) $\Rightarrow$ (2) holds for $n$ and $m$ (compared to the line above, we remove the first $\tau$ transition). We have:\\
 
@@
          {s_{3i} \OTarrow {\tau} s_{3(i+1)}}\! \in\! \mathcal{T}
-\Big)  \implies\!  {
+\Big)  \Rightarrow\!  {
 \openrule
@@
 \end{mathpar}
-First by using rule (\WTDeux) we have:
+First by using rule \WTDeux~ we have:
 \begin{mathpar}
@@
          {s_{10} \OTarrow {\tau} s_{11}} \in \mathcal{T}
-\implies 
+\Rightarrow 
 { \openrule
@@
 
-On the other hand, by rule (\WTUn) we have the following weak open transition:
+On the other hand, by rule \WTUn~ we have the following weak open transition:
 \begin{mathpar}
@@
 
-Finally by applying rule (\WTTrois) on  the above weak open transitions:
+Finally by applying rule \WTTrois~on  the above weak open transitions:
 
@@
            \vis{\set{\beta_{10}}}\!,\Pred_{10},\Post_{10}
-				 } {s_{10} \OTWeakarrow {\tau}s_{11}} \in\! \WT
+				 } {s_{10} \OTWeakarrow {\tau}s_{11}}\! \in\! \WT
 \quad
@@
 		\Pred, \Post
-				 } {s'' \OTWeakarrow {\alpha'} s'} \in\!\WT
+				 } {s'' \OTWeakarrow {\alpha'} s'}\! \in\!\WT
 \quad
@@
           \emptyset,\True,\Id(s'')
-				 } {s' \OTWeakarrow {\tau} s'} \in\! \WT
+				 } {s' \OTWeakarrow {\tau} s'}\! \in\! \WT
 \\
@@
 \Pred=\bigwedge_{i=0}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{0}\Post_{1j}}\land\\ 
-~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{i3}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{0}\Post_{1j}}\Big)\\
+~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{0}\Post_{1j}}\Big)\\
 \Post=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{0}\Post_{1j}
@@
 \end{mathpar}
-is handled trivially by rule (\WTUn). 
+is handled trivially by rule \WTUn. 
 \end{itemize}
@@
 \begin{itemize}
-\item Case rule (\WTUn). We have:
+\item Case rule \WTUn. We have:
 \begin{mathpar}
@@
            \emptyset,\True,\Id(s)
-				 } {s \OTWeakarrow {\tau} s}\! \in\! \WT
-}\!\! \Rightarrow\!\! \Big(\alpha = \tau \wedge \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
+				 } {s \OTWeakarrow {\tau} s} \in\! \WT
+}\! \Rightarrow\! \Big(\alpha = \tau \wedge \set{\gamma}=\emptyset \wedge \Pred \!=\!\True \wedge \Post =\Id(s)\wedge s\!=\!s'\Big)
 $
-\item Case rule (\WTDeux). We have:
+\item Case rule \WTDeux. We have:
 \begin{mathpar}
@@
 
-\item Case rule (\WTTrois). We have:
+\item Case rule \WTTrois. We have:
 \begin{mathpar}
@@
 
-\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau open transitions such $n_1=n+m+1$, hence by simplification we have (strictly speaking, by induction we might also have the case $\alpha=\tau\land\set \gamma=\emptyset\land \ldots$ but in this case, (\WTUn)\ allows us to obtain a similar reduction with $n_1=1$):
+\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau open transitions such $n_1=n+m+1$, hence by simplification we have (strictly speaking, by induction we might also have the case $\alpha=\tau\land\set \gamma=\emptyset\land \ldots$ but in this case, rule \WTUn~ allows us to obtain a similar reduction with $n_1=1$):
 \begin{mathpar}
@@
 \set{\gamma_2}=\mybigdotcup_{i=0}^{n_2} \vis{\set{\beta_{2i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{2 j} } }  \dotcup  \vis{\set{\beta'}\subst{\bigotimes_{j=n_2}^{0}\Post_{2j}}} \dotcup}\\~\qquad
- \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{2i}} \subst{\bigotimes_{j=i-1}^{0}\Post'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j=n_2}^{0}\Post_{2j}} }
+ \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{2i}} \subst{\bigotimes_{j=i-1}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j=n_2}^{0}\Post_{2j}} }
 \\
 \Pred_2=\bigwedge_{i=0}^{n_2}\Pred_{2i}\subst{\bigotimes_{j=i-1}^{0}\Post_{2j}}\land\Pred\,' \subst{\bigotimes_{j={n_2}}^{0}\Post_{2j}}\land\\ 
-~\qquad\quad\Big(\bigwedge_{i=0}^{m_2}\Pred\,'_{2i}\subst{\bigotimes_{j=i-1}^{0}\Post'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}}\Big)\\
-\Post_2=\bigotimes_{j=m_2}^{0}\Post'_{2j}\shortotimes\Post'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}
+~\qquad\quad\Big(\bigwedge_{i=0}^{m_2}\Pred\,'_{2i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}}\Big)\\
+\Post_2=\bigotimes_{j=m_2}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}
 $
@@
 ~~\\
-\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2} \vis{\set{\beta_{4i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{4 j} } }  \dotcup  \vis{\set{\beta'}\subst{\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}}\dotcup }\\~\!\qquad\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta_{5i}}\subst{\bigotimes_{j=i-1}^{0}\Post'_{5i}\shortotimes\Post\,'\shortotimes\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4i}} }
+\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2} \vis{\set{\beta_{4i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{4 j} } }  \dotcup  \vis{\set{\beta'}\subst{\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}}\dotcup }\\~\!\qquad\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta_{5i}}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{5i}\shortotimes\Post\,'\shortotimes\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4i}} }
 \\
@@
 \end{mathpar}
- such that  $\forall x, J'=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
+ such that  $\forall x, J'=J_{x}, (s',t_x|\Pred_{s',x})\in \mathcal{R}$; 
  and  \\
@@
      \land \alpha\!=\!\alpha_x \!\land\!  
-     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}$
+     \Pred_{s',x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}$
 
@@
          {s \OTWeakarrow {\alpha} s'} \in \WT_1
-         \implies
+         \Rightarrow
 \bigg(\forall i \in [0..n].\openrule
@@
 For the sake of simplicity, we prove the rule in the  restricted case where $n$ and $m$ are equal to $1$, hence a single tau open transition will be considered on each side of the potentially visible one.
-The proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule.
+The proof may be easily generalized to the multiple tau open transitions by using the same reasoning and \WTTrois~ rule.
 Consider each open transition separately:
@@
 \end{mathpar}
- such that  $\forall a, J_{a}=\{j\in J_1'|\beta_{1j}\neq\tau\},   (s_{11},u_a|\Pred_{s_{11},u_a})\in \mathcal{R}$ and \\
+ such that  $\forall a, J_{a}=\{j\in J_1'|\beta_{1j}\neq\tau\},   (s_{11},u_a|\Pred_{s_{11},a})\in \mathcal{R}$ and \\
  $\Pred_{s,t} \land \Pred_1\implies\\
@@
      \land\! \alpha_{1 a}\!=\!\tau \land  
-     \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$
+     \Pred_{s_{11},a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$
 
@@
 \end{mathpar}
-we have  $(s_{11},u_a|\Pred_{s_{11},u_a})\in \mathcal{R}$  and $s_{11}=s_{20}$. Again 
+we have  $(s_{11},u_a|\Pred_{s_{11},a})\in \mathcal{R}$  and $s_{11}=s_{20}$. Again 
  by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{b}^{b\in B} \subseteq \WT_2$:
@@
 such that  $\forall b, J_{b}=\{j\in J_2'|\beta_{2j}\neq\tau\}, 
-(s_{21},v_{b}|\Pred_{s_{21},v_{b}})\in \mathcal{R}$; \\
- $\Pred_{s_{11},u_a} \land \Pred_2\implies\\
+(s_{21},v_{b}|\Pred_{s_{21},b})\in \mathcal{R}$; \\
+ $\Pred_{s_{11},a} \land \Pred_2\implies\\
 \displaystyle{\bigvee_{b\in B}}
  \!\!  \left( \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}\land \Pred_{OT_{b}}\!\land \alpha'\!=\!\alpha_{2 b}\! \land\!  
-     \Pred_{s_{21},v_{b}}\subst{\Post_2\uplus\Post_{OT_{b}}}\right)$
+     \Pred_{s_{21},b}\subst{\Post_2\uplus\Post_{OT_{b}}}\right)$
 
@@
 \end{mathpar}
-From previous case, we have $(s_{21},v_{b}|\Pred_{s_{21},v_{b}})\in \mathcal{R}$, and we have $s_{21}=s_{30}$. Then, by
+From previous case, we have $(s_{21},v_{b}|\Pred_{s_{21},b})\in \mathcal{R}$, and we have $s_{21}=s_{30}$. Then, by
  Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{a}^{c\in C} \subseteq \WT_2$:
@@
  such that  $\forall c, J_{c}= \{j\in J_3'|\beta_{3j}\neq\tau\}, 
-(s_{31},w_{c}|\Pred_{s_{31},w_{c}})\in \mathcal{R}$ and \\
- $\Pred_{s_{21},v_{b}} \land \Pred_3\implies\\
+(s_{31},w_{c}|\Pred_{s_{31},c})\in \mathcal{R}$ and \\
+ $\Pred_{s_{21},b} \land \Pred_3\implies\\
 \displaystyle{\bigvee_{c\in C}}
@@
      \land\!  
-     \Pred_{s_{31},w_{c}}\subst{\Post_3\uplus\Post_{OT_{c}}}\right)$
+     \Pred_{s_{31},c}\subst{\Post_3\uplus\Post_{OT_{c}}}\right)$
 
@@
 \medskip     
-Based on cases described above by applying (\WTTrois)~rule on the resulting $\symb{WOT}$s we have:
+Based on cases described above by applying \WTTrois~rule on the resulting $\symb{WOT}$s we have:
 
@@
  \end{mathpar}
-We now need to prove that the following statement holds:\\
+It remains to be proven that the following statement holds:\\
 $\Pred_{s,t} \land \Pred\implies\\
@@
      \land \alpha \!=\! \alpha'' \land  
-     \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,})$\\
+     \Pred_{s',x}\subst{\Post_{OT}\uplus\Post\,})$\\
 We have:\\
@@
       \land  
-     \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$\\
+     \Pred_{s_{11},a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$\\
 With the conjunction of the predicate $\Pred_2\subst{\Post_1}$ on both sides of the implication, we get:\\  
@@
  \displaystyle{\bigvee_{a\in A}}
-  \!\! ( \forall j\in J_a. \vis{\beta_{1j}}=\gamma_{ja}\!  \land\! \Pred_{OT_a}\! \land\!
-     \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}) \wedge \Pred_2\subst{\Post_1\uplus\Post_{OT_a}}  \\
+  \!\! ( \forall j\in J_a. \vis{\beta_{1j}}\!=\!\gamma_{ja}\!  \land\! \Pred_{OT_a}\! \land\!
+     \Pred_{s_{11},a}\subst{\Post_1\uplus\Post_{OT_a}}) \wedge \Pred_2\subst{\Post_1\uplus\Post_{OT_a}}  \\
 $
@@
 \!\!   \left(\forall j\in J_a. \vis{\beta_{1j}}\!=\!\gamma_{ja}\land \Pred_{OT_a}
-     \!\land(\Pred_{s_{11},u_a}\wedge\Pred_2)\subst{\Post_1\uplus\Post_{OT_a}} \right)$\\
+     \!\land(\Pred_{s_{11},a}\wedge\Pred_2)\subst{\Post_1\uplus\Post_{OT_a}} \right)$\\
 By replacing the inner predicate $(\Pred_{s_{11},u_a}\wedge\Pred_2)$ by the conclusion of the  statement given in case 2,  the formula becomes: \\
@@
     \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}  \land \Pred_{OT_{b}}\!\land 
-    \alpha'\!=\!\alpha_{2 b} \land\\ \Pred_{s_{21},v_{b}}\subst{\Post_2\uplus\Post_{OT_{b}}})\subst{\Post_1\uplus\Post_{OT_a}})$\\
+    \alpha'\!=\!\alpha_{2 b} \land\\ \Pred_{s_{21},b}\subst{\Post_2\uplus\Post_{OT_{b}}})\subst{\Post_1\uplus\Post_{OT_a}})$\\
 This can be rewritten into:\\
@@
 \vis{\beta_{1j}}\!\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-(\vis{\beta_{2j}}\!=\!\gamma_{jb})\subst{\Post_1\uplus\Post_{OT_a}}   \land\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_1\uplus\Post_{OT_a}} \land  (\alpha'\!=\!\alpha_{2 b}) \subst{\Post_1\uplus\Post_{OT_a}} \land\\ \Pred_{s_{21},v_{b}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
+\vis{\beta_{2j}}\!=\!\gamma_{jb}\subst{\Post_1\uplus\Post_{OT_a}}   \land\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_1\uplus\Post_{OT_a}} \land  (\alpha'\!=\!\alpha_{2 b}) \subst{\Post_1\uplus\Post_{OT_a}} \land\\ \Pred_{s_{21},b}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
 Since $Post_1$  does not act on $\gamma_{jb}$, nor on $ \Pred_{OT_{b}}$ and $  \alpha_{2}$.
@@
 \vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-\vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jb} \subst{\Post_{OT_a}}  \land\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_{OT_a}} \land \alpha'\subst{\Post_1}=\alpha_{2 b} \subst{\Post_{OT_a}} \land\\ \Pred_{s_{21},v_b}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
+\vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jb} \subst{\Post_{OT_a}}  \land\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_{OT_a}} \land \alpha'\subst{\Post_1}=\alpha_{2 b} \subst{\Post_{OT_a}} \land\\ \Pred_{s_{21},b}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
 Finally, the conjunction with the term $\Pred_3\subst{\Post_2\shortotimes\Post_1}$ of the both sides of the implication and rewriting, we get:\\
 $(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\implies \\
-\displaystyle{\bigvee_{a\in A}} \displaystyle{\bigvee_{b\in B}} 
+\displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}} 
 (\forall j\in J_a.\vis{\beta^1_j}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
@@
 Again note that because of the domain  of the substitution is independent from some predicates and expressions, we removed $\Post_1$ and  we  added the term $\Post_{OT_{b}}\shortotimes\,\Post_{OT_a}$ in the substitution of the right side of the implication.\\
-Finally, by replacing the predicate $(\Pred_{s_{21},v_{b}} \land  \Pred_3)$
+Finally, by replacing the predicate $(\Pred_{s_{21},b} \land  \Pred_3)$
 by the conclusion of the  implication given in case 3, we get:\\
@@
  \displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}}\, \displaystyle{\bigvee_{c\in C}} 
-(\forall\! j\in\! J_a.\vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \!\in\! J_{b}.\vis{\beta_{2j}\subst{\Post_{OT_a}}}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}  \land 
+(\forall\! j\in\! J_a.\vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \!\in\! J_{b}.\vis{\beta_{2j}\subst{\Post_{OT_a}}}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}  \land \\
  \forall j\!\in\! J_{c}. \vis{\beta_{3j} \subst{\Post_2\,\shortotimes\,\Post_1}} \!=\!\gamma_{jc} \subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}  \land\\
    \underbrace{\Pred_{OT_a}\land\Pred_{OT_{b}} \subst{\Post_{OT_a}} \land 
-  \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}}_{\Pred} \land  \underbrace{\alpha'\subst{\Post_1}}_{\alpha}=\underbrace{\alpha_{2 b} \subst{\Post_{OT_a}}}_{\alpha''} \land\\ \Pred_{s_{31},w_{c}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{c}}\shortotimes \Post_{OT_{b}}\shortotimes\Post_{OT_a}}_{\Post}})$\\
+  \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}}_{\Pred} \land  \underbrace{\alpha'\subst{\Post_1}}_{\alpha}=\underbrace{\alpha_{2 b} \subst{\Post_{OT_a}}}_{\alpha''} \land\\ \Pred_{s_{31},c}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{c}}\shortotimes \Post_{OT_{b}}\shortotimes\Post_{OT_a}}_{\Post}})$\\
 The three for all statements (on $J_a$, $J_b$, and $J_c$) can be concatenated using $\dotcup$, the list union lifted to indexed sets (if $\gamma=\gamma'$ and $\gamma''=\gamma'''$ then $\gamma\dotcup\gamma''=\gamma'\dotcup\gamma'''$).\\
 $\forall j\in J_a\uplus J_b\uplus J_c.
-\vis{\beta_{1j}}\dotcup \vis{\beta_{2j}\subst{\Post_{OT_a}}}\dotcup \vis{\beta_{3j} \subst{\Post_2\,\shortotimes\,\Post_1}}= \gamma_{j a} \dotcup \gamma_{jb} \subst{\Post_{OT_a}}  \dotcup \gamma_{jc} \subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}
+\vis{\beta_{1j}}\dotcup \vis{\beta_{2j}\subst{\Post_{OT_a}}}\dotcup \vis{\beta_{3j} \subst{\Post_2\shortotimes\Post_1}}=\\ ~\hspace{5.5cm} \gamma_{j a} \dotcup \gamma_{jb} \subst{\Post_{OT_a}}  \dotcup \gamma_{jc} \subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}
 $ \\
@@
 $\Pred_{s,t} \land \Pred_{OT}\implies\\
-\displaystyle{\bigvee_{a\in A}} \displaystyle{\bigvee_{b\in B}} \displaystyle{\bigvee_{c\in C}} 
-(\forall j\in J.\gamma_j'=\gamma_j \land  \Pred \land \alpha=\alpha''  \land \Pred_{s',w_{c}}\subst{\Post_{OT}\uplus\Post\,}$\\
+\displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}}\, \displaystyle{\bigvee_{c\in C}} 
+(\forall j\in J.\gamma_j'=\gamma_j \land  \Pred \land \alpha=\alpha''  \land \Pred_{s',c}\subst{\Post_{OT}\uplus\Post\,}$\\
 
@@
  \displaystyle{\bigvee_{x\in X}} 
-(\forall j\in J.\gamma_j'=\gamma_j \land  \Pred \land \alpha=\alpha''  \land \Pred_{s',t_{x}}\subst{\Post_{OT}\uplus\Post\,}$\\
+(\forall j\in J.\gamma_j'=\gamma_j \land  \Pred \land \alpha=\alpha''  \land \Pred_{s',x}\subst{\Post_{OT}\uplus\Post\,}$\\
 \qed

### 2019-10-29 2017-Xudong-SMT/ActaInformatica.tex
ACTA INFORM Paper: Typos according to the reviews.

@@
 %\usepackage{indentfirst}
-%%%\usepackage{amsmath,amssymb,amscd,mathrsfs}
+%%%\usepackage{amsmath,amssymb,amscd,mathrsfs}f
 % \usepackage{array,booktabs,arydshln,xcolor}
@@
 	satisfiability of the predicates generated by our algorithm;
-	\item to build a prototype and validate the approach on our basic
-	case-studies, and understand the efficiency of the interaction
+	\item to build a prototype of the algorithm, and validate the approach on our basic
+	case-studies, meanwhile, understand the efficiency of the interaction
 	with the SMT solver.
@@
 SMT satisfiability (\eg \cite{DBLP:journals/jsat/AlbertiGPRR12,BruniEtAl-Tiles-Concur2000,CimattiEtAl-NUXMV-CAV2014,ChampionEtAl-Kind2-CAV2016,DBLP:conf/cade/GhilardiNRZ08}). 
-Among these works, several have shown the capacity of the SMT engines
+Among these works, several have shown the capability of the SMT engines
 (either Z3 or Yikes) as servers for solving verification conditions of
@@
 data-sensitive interaction constraints. Using an encoding of
-architectures, extended with data-dependant interactions, into open
+architectures, extended with data-dependent interactions, into open
 pNets was an interesting alternative to a direct extension to the
@@
 On top of $\mathcal{E}_\P$ we build the action algebra
-$\mathcal{A}_\P$, with $\mathcal{A}_\P\subseteq\mathcal{T}_\P,
+$\mathcal{A}_\P$, with $\mathcal{A}_\P\subseteq\mathcal{T}_\P \wedge
 \mathcal{E}_\P\cap\mathcal{A}_\P=\emptyset$;
@@
 		$e_b \in \AlgB_{\P}$ is a guard, and
-		expressions  $\AlgE_{\P}\cup\AlgA_{P}$ are assigned to $x_j$.
+		expressions  $\AlgE_{\P}\cup\AlgA_{\P}$ are assigned to $x_j$.
 		If 
@@
 		\item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
-		synchronisation vectors ($K\in\I_\P$).  It is required that each
+		synchronisation vectors ($K\in\I_\P$ where $\I_\P$ is the set of indexed
+		sets with a range depending on variables of $\P$).  It is required that each
 		$\symb{SV}_k$ is a pair $(\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k,\ g_k)$, where
@@
 The semantics of an open pNet will be defined as an open automaton, which
-is an automaton where each transition represents the composition transitions 
+is an automaton where each transition represents the composed transitions 
 of several
@@
 	An \emph{open automaton} is a tuple $
-	\langle I, J,\mathcal{S},s_0,\mathcal{T}\rangle$, where
+%	\langle I, J,\mathcal{S},s_0,\mathcal{T}\rangle$, where
+	\langle J,\mathcal{S},s_0,\mathcal{T}\rangle$, where
 	\begin{itemize}
-		\item[$\bullet$]  $I$ and $J$ are  two sets of indices,
+		%	\item[$\bullet$]  $I$ and $J$ are  two sets of indices,
+		\item[$\bullet$]  $J$ is a set of indices,
 		%	\item[$\bullet$]  $LTS_i^{i\in I}$ is a family of LTSs,
@@
 		\item[$\bullet$] $\mathcal{T}$ is a set of open transitions and, for each
-		$t\in \mathcal{T}$, there exist $I'$, $J'$ with $I'\subseteq I$, $J'
+		%   $t\in \mathcal{T}$, there exist $I'$, $J'$ with $I'\subseteq I$, $J'
+		$t\in \mathcal{T}$, there exist $J'$ with $J'
 		\subseteq J$, such that $t$ is an open transition over $J'$
@@
 \begin{example}[Open transitions]
-  Transition $OT_2$ of the pNet $EnableStateCompLeft$ is generated by
+  Transition $OT_2$ of the pNet $EnableStateCompLeft$ (shown in Figure \ref{schema:enable-composed}) is generated by
   combining the first vector of its root node with
   the second vector of its second node. The global states show that
-  controler $CState1$ is 
+  controller $CState1$ is 
   changing from state 0 to 1.
@@
           \xrightarrow{acc(x2)}_Q \} ~~
-          [\forall z. acc(x2) \neq \delta(y1)]
+          [\forall y1. acc(x2) \neq \delta(y1)]
         }
@@
 
-If we use the data-oriented pNet $EnableData$ from Figure
-\ref{schema:enable-pnets} to build a similar $EnableDataCompLeft$  expression
+If we use the data-oriented pNet $EnableData$ from Figure~\ref{schema:enable-pnets} to build a similar $EnableDataCompLeft$  expression
 ``$P>>(Q>>R)$'', the corresponding open transition would be:
@@
 $C = ({ot}_i)^{i \in [1,n]} \in \overline{comb}$ is a tuple of open transitions such that, for each $i \in [1,n]$, either $ot_i = -$, or the result action of $ot_i$ is $a_i$.
-Suppose futher that $\mathit{hole} = (b_j)^{j \in J}$ is the hole behaviour and $v$ is a fresh variable, representing the result action of the OT under construction.
+Suppose further that $\mathit{hole} = (b_j)^{j \in J}$ is the hole behaviour and $v$ is a fresh variable, representing the result action of the OT under construction.
 Then we can  build the predicate:
@@
 particular because of structured names for the fresh variables generated
-by the algorithms, allowing for tracability of the result~\cite{Avocs-RR}.
+by the algorithms, allowing for traceability of the result~\cite{Avocs-RR}.
 
@@
 in the SMTlib syntax. It contains the declaration
-of the relevent part of the LOTOS action algebra sorts 
+of the relevant part of the LOTOS action algebra sorts 
 and constructors, then the declaration of variables, and finally the
@@
 $  \begin{array}{@{}r@{}l@{}}
-    ot_1  = &\openrule{\{ \xrightarrow{a1}_P \},\\ [\forall x1. a1\neq\delta(x1)]}
-    {A_0 \xrightarrow{a1} A_0}\\
+    ot_1  = &\openrule{\{ \xrightarrow{a_1}_P \},\\ [\forall y1. a_1\neq\delta(y1)]}
+    {A_0 \xrightarrow{a_1} A_0}\\
     ot_2  =& \openrule{
-                            \{\xrightarrow{\delta(x2)}_P,\,
-                            \xrightarrow{acc(x2)}_Q\}  }
-    {A_0 \xrightarrow{\underline{\delta(x2)}} A_1}\\
+                            \{\xrightarrow{\delta(x_1)}_P,\,
+                            \xrightarrow{acc(x_1)}_Q\}  }
+    {A_0 \xrightarrow{\underline{\delta(x_1)}} A_1}\\
     ot_3  =& \openrule{
-                          \{  \xrightarrow{a3}_q \},\\ [\forall x3. a3\neq\delta(x3)] }
-    {A_1 \xrightarrow{a3} A_1}
+                          \{  \xrightarrow{a_2}_Q \},\\ [\forall y2. a_2\neq acc(y2)] }
+    {A_1 \xrightarrow{a_2} A_1}
   \end{array}$
@@
 %
-connectors specify the syncrhonisations (also called
+connectors specify the synchronisations (also called
 \emph{interactions}) between the transitions of the individual

### 2019-10-31 2016-Weak-FH-Bisim/WeakBisim.tex
Fig 1 et 2 + commentaires

--- 2019-10-29 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 Synchronisation between subnets is defined by synchronisation vectors that express how an action of a subnet can be synchronised with actions of other subnet, and how the resulting synchronised action is visible to the outside of the pNet.
-Synchronisation vectors also allow to explicitly export an action of a subnet to the next level, or to allow to subnets to synchronise and only exporting a non0observable action (provided such an non-visible action labels exist in the action algebra.
+Synchronisation vectors also allow to explicitly export an action of a subnet to the next level, or to allow to subnets to synchronise and only exporting a non-observable action (provided such an non-visible action labels exist in the action algebra.
 Finally, a pNet can leave subnets undefined and instead declare holes with a well-defined signature.
@@
 
+\subsection{Running Example}
+To illustrate this work, we use a simple communication protocol, that provides safe transport of data between two processes, over unsafe media.
+
+Fig. \ref{SimpleProt:Spec} (left) shows the example principle: two unspecified
+processes $P$ and $Q$ (holes) communicate messages, with a data value
+argument, through the two protocol entities.
+Process $P$ send an $p\_send(m)$ message to the $Sender$; this communication is denoted as $\underline{in(m)}$, where underline actions represent internal actions (similar to the $\tau$ of CCS), that cannot be further synchronised with the environment.
+At the other end process $Q$ receives the message from the $Receiver$.
+The holes $P$ and $Q$ can also have other interactions with their environment, represented here by actions $p\_a$ and $q\_b$.
+The underlying network is modelled by a medium entity transporting messages from the sender to the receiver, and that is able to detect transport errors, and signal them to the sender.
+The return $ack$ message from $receiver$ to $sender$ is supposed to be safe.
+The final transmission of the message to the recipient (Hole Q) include the value of the ``error counter'' $ec$.
+
+Fig. \ref{SimpleProt:Spec} (right) shows a graphical view of the pNet of the system \emph{specification}:
+the full system should be equivalent (e.g. through weak bisimulation)
+to the two processes connected simply through a perfect medium. Fig. \ref{SimpleProt:Spec}, right, shows the pNet representing this global specification.
+
+Fig.
+\ref{SimpleProt:Impl} show the pNet model of the protocol implementation.
+When the $Medium$ detects an error (modeled by a local $\tau$ action), it sends back a $m\_error$ message to the $Sender$.
+The $Sender$ increments its local error counter $c$, and resends the message (including $c$) to the $Medium$, that will, eventually, transmit $m,c$ to the $Receiver$.
+
 \begin{figure}[t]
@@
 \end{figure}
-
-\subsection{Running Example}
-\TODO{Rabea: trouver reference !!}
-To illustrate this work, we use a simple communication protocol, that provides safe transport of data between two processes, over unsafe media.
-The alternating bit protocol was first described in \cite{Bartlett:1969}.
-Our specification  of the ABP is based on the one given in \cite{Vergamini:1986}.
-
-Fig. \ref{SimpleProt:Spec} (left) shows the example principle: two unspecified
-processes $P$ and $Q$ (Holes) communicate messages, with a data value
-argument, through the two protocol entities $sender$ and
-$receiver$.
-The underlying network is modelled by a medium entity transporting messages from the sender to the receiver, and that is able to detect some transport error, and signal it to the sender.
-The return $ack$ message from $receiver$ to $sender$ is supposed to be safe.
-The final transmission of the message to the recipient (Hole Q) include the value of the ``error counter'' $ec$.
-
-This is only a graphical syntax,
-with an obvious semantics for building the corresponding pNets.
-
-Fig. \ref{SimpleProt:Spec} (right) shows the Schema of this system, and on the right side, its global specification, expressed as a pNet. 
-The full system should be equivalent (e.g. through weak bisimulation)
-to the two processes connected simply through a perfect medium. Fig. \ref{SimpleProt:Spec}, right, shows the pNet representing this global specification.
-
-Fig.
-\ref{SimpleProt:Impl} show the pNet model of the protocol.
-When the medium detects an error (modeled by a local $\tau$ action), it sends back a $m\_error$ message to the $Sender$.
-The $Sender$ increments its error counter $c$, and resend the message (including $c$) to the medium, that will, eventually, transmit $m,c$ to the receiver.
 
@@
    \caption{Specification pNet Schema and Specification}
-   \label{SimpleProt:Spec}
+   \label{App:SimpleProt:Spec}
 
@@
   \centerline{\includegraphics[width=12cm]{XFIG/SimpleProt-pNet}}
-  \caption{Composed pNet with the Simple Protocol Implementation}  \label{SimpleProt:Impl}
+  \caption{Composed pNet with the Simple Protocol Implementation}  \label{App:SimpleProt:Impl}
 \end{figure}

### 2019-11-02 2017-Xudong-SMT/ActaInformatica.tex
some typos corrected

@@
 
+\newcommand{\YX}[1]{{\color{red}#1}}
+
 % Volume frontmatter
@@
 	\item to separate clearly the 
-	algorithm generating the transitions of an open automaton from
-	combination of all possible (symbolic) behaviours, and from
-	the symbolic reasoning part, specifically here using an SMT
+	algorithm 
+	\YX{that generates the transitions of an open automaton from
+	the symbolic reasoning part that uses an SMT
 	engine to check the
-	satisfiability of the predicates generated by our algorithm;
+	satisfiability of the predicates generated by the algorithm;}
+
+%	\item to separate clearly the algorithm generating the transitions of an open automaton from combination of all possible (symbolic) behaviours, and from the symbolic reasoning part, specifically here using an SMT engine to check the satisfiability of the predicates generated by our algorithm;
+
 	\item to build a prototype of the algorithm, and validate the approach on our basic
@@
 SMT satisfiability (\eg \cite{DBLP:journals/jsat/AlbertiGPRR12,BruniEtAl-Tiles-Concur2000,CimattiEtAl-NUXMV-CAV2014,ChampionEtAl-Kind2-CAV2016,DBLP:conf/cade/GhilardiNRZ08}). 
-Among these works, several have shown the capability of the SMT engines
+Among these works, several have % shown the capability 
+\YX{
+demonstrated the usefulness
+of SMT engines
 (either Z3 or Yikes) as servers for solving verification conditions of
- algorithms, for large case-studies
+ algorithms, especially for large case-studies
 (\eg
 \cite{DBLP:journals/corr/abs-1806-11459,DBLP:journals/corr/CimattiGMT13}).
+}
 With
@@
 		\item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
-		synchronisation vectors ($K\in\I_\P$ where $\I_\P$ is the set of indexed
-		sets with a range depending on variables of $\P$).  It is required that each
+		synchronisation vectors, \YX{where $K\in\I_\P$ with $\I_\P$ being the set of indexed
+		sets whose ranges depend on the variables in $\P$}.  It is required that each
 		$\symb{SV}_k$ is a pair $(\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k,\ g_k)$, where
@@
                             \{\xrightarrow{\delta(y2)}_P,\,
-                            \xrightarrow{acc(y2)}_Q \}, \\
-                                        v=0, \\
+                            \xrightarrow{acc(x2)}_Q \},~
+                                        v=0,~
                                         \{v\gets 1\}}
-    {B_0 \xrightarrow{\underline{\delta(y2)}} B_1}\\
+    {B_0 \xrightarrow{\underline{\delta(x2)}} B_1}\\
     ot'_3  =& \openrule{
-                            \xrightarrow{b2}_q, \\ [\forall y2. b2\neq\delta(y2) \!\land\! v=1] }
+                            \{\xrightarrow{b2}_Q\}, ~~ [\forall y2. b2\neq\delta(y2) \!\land\! v=1] }
     {B_1 \xrightarrow{b2} B_1}
@@
 relations between the actions of the holes.
-We have shown in \cite{henrio:Forte2016} how to prove that they are bisimilar.
+We have shown in \cite{henrio:Forte2016} 
+\YX{that the two open automata are equivalent with respect to a notion of FH-bisimulation.}
+%how to prove that they are bisimilar.
 
@@
   \begin{eqnarray*}
-    OT_1 & = \openrule{\{\xrightarrow{a1}_P\}\\ a1\neq\delta(x)}
-    {\ostate{00} \xrightarrow{a1} \ostate{00}}\\
+    OT_1 & = \openrule{\{\xrightarrow{a_1}_P\}\\ a1\neq\delta(x)}
+    {\ostate{00} \xrightarrow{a_1} \ostate{00}}\\
     OT_2 & = \openrule{
@@
     OT_3 & = \openrule{
-                        \{\xrightarrow{a2}_Q\},\\a2\neq\delta(x)
+                        \{\xrightarrow{a_2}_Q\},\\a2\neq\delta(x)
                         }
-    {\ostate{10} \xrightarrow{a2} \ostate{10}}
+    {\ostate{10} \xrightarrow{a_2} \ostate{10}}
     \end{eqnarray*}
@@
                       {\ostate{10} \xrightarrow{\underline{\delta(x2)}} \ostate{11}}    \\
-    OT_5 & = \openrule{\{\xrightarrow{a3}_R\}
+    OT_5 & = \openrule{\{\xrightarrow{a_4}_R\}
     	}
-    {\ostate{11} \xrightarrow{a3} \ostate{11}}
+    {\ostate{11} \xrightarrow{a_4} \ostate{11}}
     \end{eqnarray*}

### 2019-11-03 2017-Xudong-SMT/ActaInformatica.tex
ACTA Paper: Improve Sect.2

--- 2019-10-29 2017-Xudong-SMT/ActaInformatica.tex
@@
 	with their specific decision theories;
-	\item to separate clearly the 
-	algorithm generating the transitions of an open automaton from
+	\item \QIN{to separate clearly the
+	transitions of a generated open automaton from the
 	combination of all possible (symbolic) behaviours, and from
-	the symbolic reasoning part, specifically here using an SMT
-	engine to check the
-	satisfiability of the predicates generated by our algorithm;
+	the symbolic reasoning part, specifically here, to check the
+	satisfiability of the predicates in the transitions generated by our algorithm using an SMT
+	engine;}
 	\item to build a prototype of the algorithm, and validate the approach on our basic
@@
 
-\paragraph*{Algebra presentations.}\
+\subsection{Algebra Presentations}
 In practice, the parameterisation of the pNet model by some specific
@@
 		\\\hline\specialrule{0em}{1pt}{1pt}
-		\multicolumn{3}{l}{\sl Extension for the Enable use-case of Section~\ref{section:running-example}}
+		%		\multicolumn{3}{l}{\sl Extension for the Enable use-case of Section~\ref{section:running-example}}
+		\multicolumn{3}{l}{\sl Extension for the Enable use-case of Example~\ref{example:EnableOperator}}
 		\\\hline\specialrule{0em}{1pt}{1pt}
-		Action & \texttt{ACT}, \texttt{delta, acc}  &
+		%		Action & \texttt{ACT}, \texttt{delta, acc}  &
+		Action & \texttt{l}, \texttt{r}, \texttt{$\delta$}, \texttt{acc}  &
 		\\\hline
@@
 \end{table}
+
+\QIN{
+Let us first introduce a notation in LOTOS to give an intuition how we construct the algebra presentation.
+}
+
+\begin{example}[The ``Enable'' Operator]\label{example:EnableOperator}
+\QIN{
+Suppose there are two processes $P$, $Q$.
+In the Enable expression ``$P>>Q$'', an \texttt{exit} statement within $P$ terminates the current process, carrying a value $x$ that is captured by the \texttt{accept} statement of $Q$.
+}
+
+\QIN{
+A possible encoding of such ``Enable'' operator, called $EnableState$, uses a controller $CState$ with three simple control actions $l, r, \delta$ in it to synchronise the behaviour of $P$ and $Q$.
+Here we use a simple action algebra, containing two constructors $\delta(x)$ and $acc(x)$, for any possible data type of the variable $x$, corresponding to the statements \texttt{exit} and \texttt{accept}.
+To construct the algebra presentation, we extend the triple $\APres=\langle\mathit{Sorts},\mathit{Constrs},\mathit{Ops}\rangle$ shown in Table \ref{table:BIPalgebra} with four new constructors.
+Note that the control action $\delta$ is present by the constructor $\delta$ of arity 0 here which is a different application of the constructor.
+}
+
+\QIN{
+Another possible encoding of such ``Enable'' operator, called $EnableData$, uses a data-oriented style, with a single state controller $CData$, and a state-variable $v$, with values in $\{0,1\}$.
+We can use the same algebra presentation as $EnableState$ in this case.
+}
+\end{example}
+
+Next, we enrich our example by composing two occurrences of the $EnableState$.
+In Section \ref{section:use-case:Enable} we will show how these encodings can be used to prove properties of the Enable operator.
+\begin{example}[Composition of Two ``Enable'' Operators]\label{example:ComposeEnableOperators}
+\QIN{
+Suppose there are three processes $P$, $Q$ and $R$.
+In the expression ``$P>>(Q>>R)$'', an \texttt{exit} statement within $P$ terminates the current process, carrying a value $x_1$ that is captured by the \texttt{accept} statement of $Q$ in the expression $Q>>R$.
+And then, similarly, an \texttt{exit} statement within $Q$ terminates the current process, carrying a value $x_2$ that is captured by the \texttt{accept} statement of $R$.
+}
+
+\QIN{
+We can compose two occurrences of the $EnableState$ to encode such expression.
+To distinguish the action of two controllers $CState1$ and $CState2$ used in such encoding $EnableStateCompLeft$, we names these control actions $l1, r1, \delta_1$ and $l2, r2, \delta_2$, respectively.
+The algebra presentation of $EnableStateCompLeft$ can be constructed by expending $\mathit{Constrs}$ with $\{\delta, acc, l1, l2, r1, r2, \delta_1, \delta_2\}$.
+}
+\end{example}
 
@@
 
+\begin{example}[PLTS of the Controller in the ``Enable'' Operator]
+\QIN{
+The PLTS of the controller $CState$ of the encoding $EnableState$ defined in Example \ref{example:EnableOperator} is given as a triple $\langle S,s_0, \to\rangle$ where:
+\begin{itemize}
+	\item[$\bullet$] $S=\{0, 1\}$;
+	\item[$\bullet$] $s_0=0$;
+	\item[$\bullet$] $\to=\{0\xrightarrow{l}0, 0\xrightarrow{\delta}1, 1\xrightarrow{r}1\}$.
+\end{itemize}
+Add the guard and assignment to the label of the transition, the PLTS of the controller $CData$ is given as a triple $\langle S,s_0, \to\rangle$ where:
+\begin{itemize}
+	\item[$\bullet$] $S=\{0, 1\}$;
+	\item[$\bullet$] $s_0=0$;
+	\item[$\bullet$] $\to=\{0\xrightarrow{l, v=0}0, 0\xrightarrow{\delta,  v=0, \{v\leftarrow1\}}1, 1\xrightarrow{r, v=1}1\}$.
+\end{itemize}
+}
+\end{example}
+\QIN{The PLTSs contained in $EnableStateCompLeft$ are similar to the PLTS $CState$.}
+
 Now, we define
@@
 
+\begin{example}[pNet of the ``Enable'' Operator]\label{example:pNetEnable}
+\QIN{
+Consider the encoding $EnableState$ defined in Example \ref{example:EnableOperator}, the processes $P$ and $Q$ are holes of the pNet.} In this example we use \emph{synchronised actions}, to express actions that cannot be further synchronised, similar to the silent action $\tau$ of CCS.
+We denote them as any action expression with the text underlined, as e.g.
+$\underline{\delta(x_1)}$.
+Such synchronised actions do not play any special role for defining the semantics of pNets, but as one can expect, will be crucial for defining weak equivalences.
+\QIN{The pNet can be given as follow:
+\begin{itemize}
+	\item[$\bullet$] $\pNet=\{CState\}$;
+	\item[$\bullet$] $J=\{P, Q\}$;
+	\item[$\bullet$] $\symb{SV}=\{\langle a_1, \text{-}, l\rangle\rightarrow a_1[\forall y1.a_1\neq \delta(y1)], 
+	\langle \delta(x_1), acc(x_1), \delta\rangle\rightarrow\underline{\delta(x_1)},\\
+	\langle \text{-}, a_2, r\rangle\rightarrow a_2[\forall y2.a_2\neq acc(y2)]\}$.
+\end{itemize}
+Replace $CState$ with $CData$ the pNet of $EnableData$ can be given with similar $\symb{SV}$.
+}
+\end{example}
+
+Note that synchronisation vectors are defined in a parameterised
+manner:  the first and third lines represent one vector
+for each possible action of hole $P$
+(resp. $Q$). This notation can also use predicates, as in the first
+case, in which we want the vector to apply to any action of $P$
+except for $\delta(z)$.
+
+\QIN{The pNet of $EnableStateCompLeft$ presents a bigger tree with three levels containing a pNet as its node.}
+\begin{example}[pNet of the Composition of ``Enable'' Operators]\label{example:pNetComposeEnable}
+\QIN{
+Consider the encoding $EnableStateCompLeft$ defined in Example \ref{example:ComposeEnableOperators}, the processes $P$, $Q$ and $R$ are holes of the pNet.
+Let $pNet_1$ be the sub-pNet that presents $Q>>R$.
+The pNet can be given as follow:
+\begin{itemize}
+	\item[$\bullet$] $\pNet=\{pNet_1, CState1\}$;
+	\item[$\bullet$] $J=\{P\}$;
+	\item[$\bullet$] $\symb{SV}=\{\langle a_1, \text{-}, l1\rangle\rightarrow a_1[\forall y1.a_1\neq \delta(y1)], 
+	\langle \delta(x_1), acc(x_1), \delta\rangle\rightarrow\underline{\delta(x_1)},\\
+	\langle \text{-}, a_2, r1\rangle\rightarrow a_2[\forall y2.a_2\neq acc(y2)]\}.$
+\end{itemize}
+The sub-pNet $pNet_1$ is a pNet of a single ``Enable'' operator as the pNet in Example \ref{example:pNetEnable}.
+Actions in $pNet_1$ should be renamed to distinguish themselves from those already used in the pNet of $EnableStateCompLeft$.
+}
+\end{example}
+
 In Figures~\ref{schema:enable-pnets},\ref{schema:enable-composed}, we show
@@
 
-\subsection{Example}
-\label{section:running-example}
+%\subsection{Example}
+%\label{section:running-example}
 
@@
 
-	To give an intuition of the open pNet model and its semantics, we use
-	here a simple example based on the ``Enable'' operator of the LOTOS language.
-	In the Enable expression ``$P>>Q$'', an \texttt{exit} statement within $P$
-	terminates the current process, carrying a value $x$ that
-	is captured by the \texttt{accept} statement of $Q$. 	
-	We use a simple action algebra,
-	containing two constructors $\delta(x)$ and $acc(x)$, for any
-	possible data type of the variable $x$, corresponding to the
-	statements \texttt{exit} and \texttt{accept}. 
-	We need no specific predicate over the action expressions, apart
-	from equality of actions.
-
-	In Figure \ref{schema:enable-pnets}, we show two possible encodings of the  
-	``Enable'' operator.
-        In the first encoding $EnableState$, in the upper part of
-	Figure \ref{schema:enable-pnets}, we use a controller $CState$ with two
-	states, and simple control actions $l, r, \delta$. The second encoding
-	$EnableData$ uses a data-oriented style, with a single state controller $CData$, and a
-	state-variable $v$, with values in $\{0,1\}$.
-
-        In this example we use \emph{synchronised
-          actions}, to express actions that cannot be further synchronised, similar to the
-         silent action $\tau$ of CCS. We denote them as any action expression with the text
-        underlined, as e.g. $\underline{\delta(x_2)}$. Such
-        synchronised actions do not play any special role for defining
-        the semantics of pNets, but as one can expect, will be crucial
-        for defining weak equivalences.
-
-	Note that synchronisation vectors are defined in a parameterised
-	manner:  the first and third lines represent one vector
-	for each possible action of hole $P$
-	(resp. $Q$). This notation can also use predicates, as in the first
-	case, in which we want the vector to apply to any action of $P$
-	except for $\delta(z)$.
-
-	In Figure \ref{schema:enable-composed}, we enrich our example by
-	composing two occurences of the $EnableState$ pNet. In Section
-        \ref{section:use-case:Enable} we will show how these encodings can
-        be used to prove properties of the Enable operator.
+%	To give an intuition of the open pNet model and its semantics, we use
+%	here a simple example based on the ``Enable'' operator of the LOTOS language.
+%	In the Enable expression ``$P>>Q$'', an \texttt{exit} statement within $P$
+%	terminates the current process, carrying a value $x$ that
+%	is captured by the \texttt{accept} statement of $Q$. 	
+%	We use a simple action algebra,
+%	containing two constructors $\delta(x)$ and $acc(x)$, for any
+%	possible data type of the variable $x$, corresponding to the
+%	statements \texttt{exit} and \texttt{accept}. 
+%	We need no specific predicate over the action expressions, apart
+%	from equality of actions.
+%        
+%	In Figure \ref{schema:enable-pnets}, we show two possible encodings of the  
+%	``Enable'' operator.
+%        In the first encoding $EnableState$, in the upper part of
+%	Figure \ref{schema:enable-pnets}, we use a controller $CState$ with two
+%	states, and simple control actions $l, r, \delta$. The second encoding
+%	$EnableData$ uses a data-oriented style, with a single state controller $CData$, and a
+%	state-variable $v$, with values in $\{0,1\}$.
+%
+%        In this example we use \emph{synchronised
+%          actions}, to express actions that cannot be further synchronised, similar to the
+%         silent action $\tau$ of CCS. We denote them as any action expression with the text
+%        underlined, as e.g. $\underline{\delta(x_2)}$. Such
+%        synchronised actions do not play any special role for defining
+%        the semantics of pNets, but as one can expect, will be crucial
+%        for defining weak equivalences.
+%	
+%	Note that synchronisation vectors are defined in a parameterised
+%	manner:  the first and third lines represent one vector
+%	for each possible action of hole $P$
+%	(resp. $Q$). This notation can also use predicates, as in the first
+%	case, in which we want the vector to apply to any action of $P$
+%	except for $\delta(z)$.
+%	
+%	In Figure \ref{schema:enable-composed}, we enrich our example by
+%	composing two occurences of the $EnableState$ pNet. In Section
+%        \ref{section:use-case:Enable} we will show how these encodings can
+%        be used to prove properties of the Enable operator.
 
@@
     ot'_1  =& \openrule{
-    	\{\xrightarrow{b1}_P\}, ~~ [\forall y1. b1\neq\delta(y1) \!\land\! v=0]}
-    {B_0 \xrightarrow{b1} B_0}\\
+    	\{\xrightarrow{b_1}_P\}, ~~ [\forall y1. b_1\neq\delta(y1) \!\land\! v=0]}
+    {B_0 \xrightarrow{b_1} B_0}\\
     ot'_2  =& \openrule{
-                            \{\xrightarrow{\delta(y2)}_P,\,
-                            \xrightarrow{acc(y2)}_Q \}, \\
-                                        v=0, \\
+                            \{\xrightarrow{\delta(y_2)}_P,\,
+                            \xrightarrow{acc(x_2)}_Q \},~
+                                        v=0,~
                                         \{v\gets 1\}}
-    {B_0 \xrightarrow{\underline{\delta(y2)}} B_1}\\
+    {B_0 \xrightarrow{\underline{\delta(x_2)}} B_1}\\
     ot'_3  =& \openrule{
-                            \xrightarrow{b2}_q, \\ [\forall y2. b2\neq\delta(y2) \!\land\! v=1] }
-    {B_1 \xrightarrow{b2} B_1}
+                            \{\xrightarrow{b_2}_Q\}, ~~ [\forall y2. b_2\neq acc(y2) \!\land\! v=1] }
+    {B_1 \xrightarrow{b_2} B_1}
   \end{array}$
@@
   \begin{eqnarray*}
-    OT_1 & = \openrule{\{\xrightarrow{a1}_P\}\\ a1\neq\delta(x)}
-    {\ostate{00} \xrightarrow{a1} \ostate{00}}\\
+    OT_1 & = \openrule{\{\xrightarrow{a_1}_P\}\\ a_1\neq\delta(x)}
+    {\ostate{00} \xrightarrow{a_1} \ostate{00}}\\
     OT_2 & = \openrule{
-                            \{\xrightarrow{\delta(x1)}_P, ~~
-                            \xrightarrow{acc(x1)}_Q\}
+                            \{\xrightarrow{\delta(x_1)}_P, ~~
+                            \xrightarrow{acc(x_1)}_Q\}
                       }
-                      {\ostate{00} \xrightarrow{\underline{\delta(x1)}} \ostate{10}}    \\
+                      {\ostate{00} \xrightarrow{\underline{\delta(x_1)}} \ostate{10}}    \\
     OT_3 & = \openrule{
-                        \{\xrightarrow{a2}_Q\},\\a2\neq\delta(x)
+                        \{\xrightarrow{a_2}_Q\},\\a_2\neq\delta(x)
                         }
-    {\ostate{10} \xrightarrow{a2} \ostate{10}}
+    {\ostate{10} \xrightarrow{a_2} \ostate{10}}
     \end{eqnarray*}
@@
     OT_4 & = \openrule{
-                      \{\xrightarrow{\delta(x2)}_Q, \qquad 
-                       \xrightarrow{acc(x2)}_R\} 
+                      \{\xrightarrow{\delta(x_2)}_Q, \qquad 
+                       \xrightarrow{acc(x_2)}_R\} 
                        }
-                      {\ostate{10} \xrightarrow{\underline{\delta(x2)}} \ostate{11}}    \\
-    OT_5 & = \openrule{\{\xrightarrow{a3}_R\}
+                      {\ostate{10} \xrightarrow{\underline{\delta(x_2)}} \ostate{11}}    \\
+    OT_5 & = \openrule{\{\xrightarrow{a_4}_R\}
     	}
-    {\ostate{11} \xrightarrow{a3} \ostate{11}}
+    {\ostate{11} \xrightarrow{a_4} \ostate{11}}
     \end{eqnarray*}

### 2019-11-03 2017-Xudong-SMT/ActaInformatica.tex

@@
 	with their specific decision theories;
-	\item \QIN{to separate clearly the
-	transitions of a generated open automaton from the
-	combination of all possible (symbolic) behaviours, and from
-	the symbolic reasoning part, specifically here, to check the
-	satisfiability of the predicates in the transitions generated by our algorithm using an SMT
-	engine;}
+	\item to separate clearly the 
+	algorithm 
+	\YX{that generates the transitions of an open automaton from
+	the symbolic reasoning part that uses an SMT
+	engine to check the
+	satisfiability of the predicates generated by the algorithm;}
+
+%	\item to separate clearly the algorithm generating the transitions of an open automaton from combination of all possible (symbolic) behaviours, and from the symbolic reasoning part, specifically here using an SMT engine to check the satisfiability of the predicates generated by our algorithm;
 	\item to build a prototype of the algorithm, and validate the approach on our basic

### 2019-11-04 2017-Xudong-SMT/ActaInformatica.tex
ACTA Paper: Add example of FUN in Example 1 and supplement in page 20.

@@
 Here we use a simple action algebra, containing two constructors $\delta(x)$ and $acc(x)$, for any possible data type of the variable $x$, corresponding to the statements \texttt{exit} and \texttt{accept}.
-To construct the algebra presentation, we extend the triple $\APres=\langle\mathit{Sorts},\mathit{Constrs},\mathit{Ops}\rangle$ shown in Table \ref{table:BIPalgebra} with four new constructors.
+To construct the algebra presentation, we extend the triple $\APres=\langle\mathit{Sorts},\mathit{Constrs},\mathit{Ops}\rangle$ shown in Table \ref{table:BIPalgebra} with four new constructors.}
+
+\QIN{Using the \texttt{FUN} constructor, we express the custom constructors such as $\delta(x)$ in the form of $\texttt{FUN}_{Action, Data}(\delta, x)$ where $x$ is a variable of type $Data$.
+Here we have $arity(\texttt{FUN}_{Action, Data})=2$ and $\texttt{FUN}_{Action, Data}: Action, Data\to Action$.
 Note that the control action $\delta$ is present by the constructor $\delta$ of arity 0 here which is a different application of the constructor.
@@
 Another possible encoding of such ``Enable'' operator, called $EnableData$, uses a data-oriented style, with a single state controller $CData$, and a state-variable $v$, with values in $\{0,1\}$.
-We can use the same algebra presentation as $EnableState$ in this case.
+As there is no more constructor required, we can use the same algebra presentation as $EnableState$ in this case.
 }
@@
 for several examples, starting with three constructions from
-Section~\ref{section:running-example} using the Enable operator.
+Section~\ref{section:pnets} using the Enable operator.
 Then we give detailed results for the Failure Controller that was
@@
 Figure~\ref{schema:enable-OAs}. 
+\QIN{The initial transition of $EnableData$ is transformed to the initialisation of the state variables, here is $\{v\leftarrow1\}$, for its open automata.}
 Note that although these automata look very similar to the PLTS

### 2019-11-04 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf. paper: Adjust MkPred on page 9&12. Improve content on page 12.
In Paragraph Predicate.
In Paragraph Filtering.

@@
 the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
-\begin{multline*}
-	\MkPred(SV_k, a_i^{i\in I}, b_j^{j\in J}, v)\Longleftrightarrow
-	%% \begin{array}{l}
-	\exists {(a'_i)}^{i\in I},
-	{(b'_j)}^{j\in J},v'.\\
-	SV_k={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v'
-	\land
-	\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v' . 
-\end{multline*}
+%\begin{multline*}
+%	\MkPred(SV_k, a_i^{i\in I}, b_j^{j\in J}, v)\Longleftrightarrow
+%	%% \begin{array}{l}
+%	\exists {(a'_i)}^{i\in I},
+%	{(b'_j)}^{j\in J},v'.\\
+%	SV_k={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v'
+%	\land
+%	\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v' . 
+%\end{multline*}
+$$\MkPred(SV_k, a_i^{i\in I}, b_j^{j\in J}, v)\Longleftrightarrow SV_k={(a_i)}^{i\in I}, {(b_j)}^{j\in J}\rightarrow v.$$
 
@@
 Suppose that $sv = \left((a'_i)^{i\in I} (b'_j)^{j\in J}\rightarrow v'\right) \in SV$ is a synchronisation vector, $G_k$ is its guard, and
-$C = ({ot}_i)^{i \in [1,n]} \in \overline{comb}$ is a tuple of open transitions such that, for each $i \in [1,n]$, either $ot_i = -$, or the result action of $ot_i$ is $a_i$.
+$c = ({ot}_i)^{i \in [1,n]} \in \overline{comb}$ is a tuple of open transitions such that, for each $i \in [1,n]$, either $ot_i = -$, or the result action of $ot_i$ is $a_i$.
 Suppose further that $\mathit{hole} = (b_j)^{j \in J}$ is the hole behaviour and $v$ is a fresh variable, representing the result action of the OT under construction.
@@
 \begin{multline*}
-  \mathit{MkPred}(sv, C, \overline{\mathit{hole}}) = 
+  \mathit{MkPred}(sv, c, \overline{\mathit{hole}}, v) = 
   (\forall i\in I, a_i=a'_i) \land
@@
 While matching a vector with a combination tuple, \emph{Matching}
-tries to filter out some incompatibilities; there may be several
-reasons why the matching would fail: 
-\begin{itemize}
-  \item if some subnet is marked as inactive in the vector, and the
-    chosen combination has an active behaviour at this position, or vice-versa;
-  \item if some subnet action expression in the vector does not match (by
-    pattern-matching) with the corresponding action expression in $C$;
-  \item or if the whole set of active subnet actions in the vector
-    cannot be matched (by unification) with the corresponding action expressions
-      in the tuple $C$ (this is strictly stronger than the
-      previous filter). 
-\end {itemize}
-
-Even when unification succeeds, it is still possible that
-the resulting predicate would be unsatisfiable, because of some
-incompatibility involving the guards. In our algorithm, we choose to
-apply only the simplest filter inside the \emph{Matching} method
-(before applying the predicate and OT construction). Matching and
-unification  will be checked later, together with the guards collected
-from synchronisation vectors and from PLTS transtions, using the
-satisfiability check in the SMT engine.
+tries to filter out some incompatibilities \QIN{in advance.
+If some of the subnet actions are marked inactive in the vector while some of the behaviours at the corresponding positions in the chosen combination are active, the matching would fail and the algorithm can filter it.}
+
+\QIN{The matching would also fail if the active actions in the vector and the active behaviours in the chosen combination are not matched by pattern-matching or unification.
+Such case will be checked later, together with the guards collected from synchronisation vectors and from PLTS transtions, using the satisfiability check in the SMT engine.}
+
+%; there may be several
+%reasons why the matching would fail: 
+%\begin{itemize}
+%  \item if some subnet is marked as inactive in the vector, and the
+%    chosen combination has an active behaviour at this position, or vice-versa;
+%  \item if some subnet action expression in the vector does not match (by
+%    pattern-matching) with the corresponding action expression in $C$;
+%  \item or if the whole set of active subnet actions in the vector
+%    cannot be matched (by unification) with the corresponding action expressions
+%      in the tuple $C$ (this is strictly stronger than the
+%      previous filter). 
+%\end {itemize}
+
+%Even when unification succeeds, it is still possible that
+%the resulting predicate would be unsatisfiable, because of some
+%incompatibility involving the guards. In our algorithm, we choose to
+%apply only the simplest filter inside the \emph{Matching} method
+%(before applying the predicate and OT construction). Matching and
+%unification  will be checked later, together with the guards collected
+%from synchronisation vectors and from PLTS transtions, using the
+%satisfiability check in the SMT engine.
 
@@
 Our matching/filtering strategy builds some transitions where
-the predicates express incompatible constraints. Even if having an
+the predicates express incompatible constraints. 
+\QIN{Such constraints come from the mismatching of the actions by pattern-matching or unification, involving the guards, which are all presented in the predicates.}
+Even if having an
 unsatisfiable (symbolic) transition would not be incorrect,
@@
 
-\emph{Translation of action algebra presentation.}
+\paragraph{Translation of action algebra presentation.}
 In~\cite{AVOCS18}, we  define the translation of an algebra presentation into
@@
 
-\emph{Translation of open transitions.}
+\paragraph{Translation of open transitions.}
 In~\cite{Avocs-RR} we formally define all steps of the translation of each

### 2019-11-05 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf. paper: Improve the beginning of Sect.4.3.

@@
 Suppose that $sv = \left((a'_i)^{i\in I} (b'_j)^{j\in J}\rightarrow v'\right) \in SV$ is a synchronisation vector, $G_k$ is its guard, and
-$c = ({ot}_i)^{i \in [1,n]} \in \overline{comb}$ is a tuple of open transitions such that, for each $i \in [1,n]$, either $ot_i = -$, or the result action of $ot_i$ is $a_i$.
+$comb = ({ot}_i)^{i \in [1,n]} \in \overline{comb}$ is a tuple of open transitions such that, for each $i \in [1,n]$, either $ot_i = -$, or the result action of $ot_i$ is $a_i$.
 Suppose further that $\mathit{hole} = (b_j)^{j \in J}$ is the hole behaviour and $v$ is a fresh variable, representing the result action of the OT under construction.
@@
 \begin{multline*}
-  \mathit{MkPred}(sv, c, \overline{\mathit{hole}}, v) = 
+  \mathit{MkPred}(sv, comb, \overline{\mathit{hole}}, v) = 
   (\forall i\in I, a_i=a'_i) \land
@@
 
-The set $L1$ may contain unreachable transitions. To remove those
-transitions, the last step of the  
+\QIN{As the removal of the unsatisfiable transitions leads to some transitions losing their pioneer transitions, }
+the set $L1$ may contain unreachable transitions. To remove those transitions, the last step of the  
 algorithm (lines 12-14) builds the final open automaton via a traversal of $L1$,
@@
 In practice, this could be
-expensive, and it is not incorrect to leave some UNSAT OTs in the
-result. From a  practical point of view, very little will be gained to compute the
-fixed point, so we would only perform one step of iteration. Further algorithms 
+expensive \QIN{as it needs several times of traversal of the whole set of open transitions}, and it is not incorrect to leave some UNSAT OTs in the
+result.
+\QIN{From a  practical point of view, the unreachable transitions is usually a small part of result open transitions, very little will be gained to compute the fixed point.
+So we would only perform one step of iteration.} Further algorithms
 (e.g. model-checking or equivalence checking) will be able to use the

### 2019-11-05 2017-Xudong-SMT/ActaInformatica.tex
running ex, and decidability

--- 2019-11-04 2017-Xudong-SMT/ActaInformatica.tex
@@
 for denoting actions, nor any specific communication mechanism. So we
-leave unspecified the constructors of the algebra that will allow building
+leave unspecified the constructors of the algebraused to build
 expressions and actions. Moreover, we use a generic {\em action interaction}
@@
 further synchronised with the environment. It also comes with an
-overloaded \texttt{FUN} constructor, used to build actions with
+overloaded \texttt{FUN} constructor, used to build action expressions with
 arguments, which will be instantiated to the required sorts for a given
@@
 
-\QIN{
-Let us first introduce a notation in LOTOS to give an intuition how we construct the algebra presentation.
+\subsection{Running example: the Enable operator}
+\ERIC{To illustrate our definitions and results, we will use a small running example, coming from the specification language LOTOS \cite{LotosISO89}.
+  Suppose we have two unspecified processes $P$ and $Q$.
+In the Enable expression ``$P>>Q$'', an \texttt{exit} statement within $P$ terminates the current process and pass the control to $Q$, carrying a value $x$ that is captured by the \texttt{accept} statement of $Q$.
+  In the next section we will define pNet encodings of the Enable operator. Let us start by defining the algebra presentation that will be used in these pNets.
 }
@@
 \begin{example}[The ``Enable'' Operator]\label{example:EnableOperator}
-\QIN{
-Suppose there are two processes $P$, $Q$.
-In the Enable expression ``$P>>Q$'', an \texttt{exit} statement within $P$ terminates the current process, carrying a value $x$ that is captured by the \texttt{accept} statement of $Q$.
+\ERIC{In Fig. \ref{schema:enable-pnets} we shall give two possible pNet  encodings of the ``Enable'' operator respectively state-oriented and data-oriented. 
+The first one is called $EnableState$, and uses a controller $CState$ with three simple control actions $l, r, \delta$ in it to synchronise the behaviour of $P$ and $Q$.
+Here we use a simple action algebra, containing two constructors $\delta(x)$ and $acc(x)$, for any possible data type of the variable $x$, corresponding to the LOTOS statements \texttt{exit} and \texttt{accept}.
+To construct the algebra presentation, we extend the triple $\APres=\langle\mathit{Sorts},\mathit{Constrs},\mathit{Ops}\rangle$ shown in Table \ref{table:BIPalgebra} with four new action constant constructors $l, r, \delta, acc$.}
+
+\ERIC{This shows an example of the generic ``FUN'' constructor used to construct expressions (of the Action sort, or of any data sort) in any algebra presentations.
+  Here \texttt{FUN} will be instanciated e.g. as, $\delta(x)$ in the form of $\texttt{FUN}_{Action, Data}(\delta, x)$ where $x$ is a variable of type $Data$.
+  %Here we have $arity(\texttt{FUN}_{Action, Data})=2$ and $\texttt{FUN}_{Action, Data}: Action, Data\to Action$.
+  Note that the same action constructor $\delta$ is also used as a constant action in the controller $CState$.
 }
 
-\QIN{
-A possible encoding of such ``Enable'' operator, called $EnableState$, uses a controller $CState$ with three simple control actions $l, r, \delta$ in it to synchronise the behaviour of $P$ and $Q$.
-Here we use a simple action algebra, containing two constructors $\delta(x)$ and $acc(x)$, for any possible data type of the variable $x$, corresponding to the statements \texttt{exit} and \texttt{accept}.
-To construct the algebra presentation, we extend the triple $\APres=\langle\mathit{Sorts},\mathit{Constrs},\mathit{Ops}\rangle$ shown in Table \ref{table:BIPalgebra} with four new constructors.}
-
-\QIN{Using the \texttt{FUN} constructor, we express the custom constructors such as $\delta(x)$ in the form of $\texttt{FUN}_{Action, Data}(\delta, x)$ where $x$ is a variable of type $Data$.
-Here we have $arity(\texttt{FUN}_{Action, Data})=2$ and $\texttt{FUN}_{Action, Data}: Action, Data\to Action$.
-Note that the control action $\delta$ is present by the constructor $\delta$ of arity 0 here which is a different application of the constructor.
-}
-
-\QIN{
-Another possible encoding of such ``Enable'' operator, called $EnableData$, uses a data-oriented style, with a single state controller $CData$, and a state-variable $v$, with values in $\{0,1\}$.
+\ERIC{The $EnableData$ pNet will use the same algebra presentation.}
+%\QIN{
+%Another possible encoding of such ``Enable'' operator, called $EnableData$, uses a data-oriented style, with a single state controller $CData$, and a state-variable $v$, with values in $\{0,1\}$.
 As there is no more constructor required, we can use the same algebra presentation as $EnableState$ in this case.
-}
-\end{example}
-
-Next, we enrich our example by composing two occurrences of the $EnableState$.
-In Section \ref{section:use-case:Enable} we will show how these encodings can be used to prove properties of the Enable operator.
-\begin{example}[Composition of Two ``Enable'' Operators]\label{example:ComposeEnableOperators}
-\QIN{
-Suppose there are three processes $P$, $Q$ and $R$.
-In the expression ``$P>>(Q>>R)$'', an \texttt{exit} statement within $P$ terminates the current process, carrying a value $x_1$ that is captured by the \texttt{accept} statement of $Q$ in the expression $Q>>R$.
-And then, similarly, an \texttt{exit} statement within $Q$ terminates the current process, carrying a value $x_2$ that is captured by the \texttt{accept} statement of $R$.
-}
-
-\QIN{
-We can compose two occurrences of the $EnableState$ to encode such expression.
-To distinguish the action of two controllers $CState1$ and $CState2$ used in such encoding $EnableStateCompLeft$, we names these control actions $l1, r1, \delta_1$ and $l2, r2, \delta_2$, respectively.
-The algebra presentation of $EnableStateCompLeft$ can be constructed by expending $\mathit{Constrs}$ with $\{\delta, acc, l1, l2, r1, r2, \delta_1, \delta_2\}$.
-}
+%}
 \end{example}
@@
 Each state has its set of variables called \emph{state variables}, 
-which can only be modified by the assignment in transitions targeting this state. 
-A global state variable of a PLTS is a state variable defined in all states.
+which can only be modified by the assignment in transitions targeting this state. Variables of the initial state must be initialized.
+%Eric: I have removed the mention of ``global variables''. Do we use them somewhere else in the paper ? I did not find any.}
+%A global state variable of a PLTS is a state variable defined in all states.
 % $x$ satisfying $\forall s\!\in\! S .\, x\!\in\! \vars(s)$. 
@@
 We first define the set of actions a PLTS can use.  Let $a$
-range over action labels, $\symb{op}$ over operators, and $x_i$  over
+range over action constants, $\symb{op}$ over operators, and $x$  over
 variable names. Action terms are given by the following grammar:
@@
 \begin{example}[PLTS of the Controller in the ``Enable'' Operator]
-\QIN{
-The PLTS of the controller $CState$ of the encoding $EnableState$ defined in Example \ref{example:EnableOperator} is given as a triple $\langle S,s_0, \to\rangle$ where:
+\ERIC{
+The PLTS of the controller $CState$ from Example \ref{example:EnableOperator} is  $\langle S,s_0, \to\rangle$, where:
 \begin{itemize}
-	\item[$\bullet$] $S=\{0, 1\}$;
-	\item[$\bullet$] $s_0=0$;
+	\item[$\bullet$] $S=\{0, 1\}$, $s_0=0$;
 	\item[$\bullet$] $\to=\{0\xrightarrow{l}0, 0\xrightarrow{\delta}1, 1\xrightarrow{r}1\}$.
 \end{itemize}
-Add the guard and assignment to the label of the transition, the PLTS of the controller $CData$ is given as a triple $\langle S,s_0, \to\rangle$ where:
+Featuring guards and assignments in the label of transitions, the PLTS of the controller $CData$ is $\langle S,s_0, \to\rangle$ where:
 \begin{itemize}
-	\item[$\bullet$] $S=\{0, 1\}$;
-	\item[$\bullet$] $s_0=0$;
-	\item[$\bullet$] $\to=\{0\xrightarrow{l, v=0}0, 0\xrightarrow{\delta,  v=0, \{v\leftarrow1\}}1, 1\xrightarrow{r, v=1}1\}$.
+	\item[$\bullet$] $S=\{0, 1\}$, $s_0=0$, $vars(s_0)=\{v\}$, $\texttt{init}\ \{v:=0\}$;
+	\item[$\bullet$] $\to=\{0\xrightarrow{l, [v=0]}0, 0\xrightarrow{\delta,  [v=0], \{v\leftarrow1\}}1, 1\xrightarrow{r, [v=1]}1\}$.
 \end{itemize}
 }
+\ERIC{The PLTSs contained in $EnableStateCompLeft$ are similar to the PLTS $CState$, but their action constants have been renamed, ensuring disjoint state variable sets.}
 \end{example}
-\QIN{The PLTSs contained in $EnableStateCompLeft$ are similar to the PLTS $CState$.}
+
+\begin{figure}[t]
+\begin{minipage}{6.1cm}
+
+  \includegraphics[width=\linewidth]{ActaXFIG/Enable1}
+  \\[1.3ex]
+ \includegraphics[width=\linewidth]{ActaXFIG/Enable2}
+  \caption{Two pNet encodings for  Enable }  \label{schema:enable-pnets}
+\end{minipage}
+  \hspace{2mm}
+\begin{minipage}{6cm}
+  \includegraphics[width=\linewidth]{ActaXFIG/P-QR}
+  \caption{Composed pNet for ``$P>>(Q>>R)$''}  \label{schema:enable-composed}
+\end{minipage}
+
+\end{figure}
 
@@
 expose a single resulting global action.
-
-%% \begin{definition}[pNets]\label{def-pnets}
-%% A pNet is a hierarchical structure, whereof the leaves are PLTSs and holes:
-%% $\pNet::= PLTS~|~\langle \pNet_i^{i\in I}, S_j^{j\in J}, \symb{SV}_k^{k\in K}\rangle$,
-%% where
-%% \begin{itemize}
-%% \item[$\bullet$] %\noteEM{Pire que ca, $\I$ n'est pas
-%%                  %defini...}\noteSB{Why is one $\I$ and the other
-%%   %$\I_\P$?}
-%%   $I$ and $J$ are the sets over which are indexed sub-pNets and holes, respectively, such that: $I\cap J=\emptyset$ and  $I\cup J\neq\emptyset$.
-
-%% \item[$\bullet$] $\pNet_i^{i\in I}$ is a family of sub-pNets.
-
-%% \item[$\bullet$] $S_j \subseteq \AlgA$ is a set of action terms,
-%%   denoting the $\Sort$\footnote{The definition of $Sorts$ (the
-%%     set of actions of a Hole  
-%%   or pNet), and also of $Leaves$ and $Holes$ (respectively all PLTSs
-%%   and all holes in a pNet), can be found in \cite{henrio:Forte2016}.}
-%%   of hole $j$.
-
-%% \item[$\bullet$] $\symb{SV}_k^{k\in K}$, with $K\in\I_\P$, is a set of
-%%   synchronisation vectors: for each $k\!\in\! K$,
-%%   $\symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k$ where
-%%   $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
-%%   $\forall i\!\in\! I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$
-%% %  \noteSB{What is the sort of a pNet? Should we define $\Sort(\pNet)
-%% %    \triangleq \{\Label(\symb{SV}_k\,|\,k \in K\}$?}
-%%   , 
-%%   $\forall j\!\in\!
-%%   J_k.\,\alpha_{j}\!\in\!S_j$, and $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
-%%   J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
-%%   $\Label(\symb{SV}_k) = \alpha'_k$.
-%% \end{itemize}
-%% \end{definition}
 
@@
 
+%% Next, we enrich our example by composing two occurrences of the $EnableState$.
+In Section \ref{section:use-case:Enable} we will show how these encodings can be used to prove properties of the Enable operator.
+%% \begin{example}[Composition of Two ``Enable'' Operators]\label{example:ComposeEnableOperators}
+%% \QIN{
+%% Suppose there are three processes $P$, $Q$ and $R$.
+In the expression ``$P>>(Q>>R)$'', an \texttt{exit} statement within $P$ terminates the current process, carrying a value $x_1$ that is captured by the \texttt{accept} statement of $Q$ in the expression $Q>>R$.
+And then, similarly, an \texttt{exit} statement within $Q$ terminates the current process, carrying a value $x_2$ that is captured by the \texttt{accept} statement of $R$.
+%% }
+%% \QIN{
+%% We can compose two occurrences of the $EnableState$ to encode such expression.
+To distinguish the action of two controllers $CState1$ and $CState2$ used in such encoding $EnableStateCompLeft$, we names these control actions $l1, r1, \delta_1$ and $l2, r2, \delta_2$, respectively.
+The algebra presentation of $EnableStateCompLeft$ can be constructed by expending $\mathit{Constrs}$ with $\{\delta, acc, l1, l2, r1, r2, \delta_1, \delta_2\}$.
+%% }
+%% \end{example}
+
 \begin{example}[pNet of the ``Enable'' Operator]\label{example:pNetEnable}
-\QIN{
-Consider the encoding $EnableState$ defined in Example \ref{example:EnableOperator}, the processes $P$ and $Q$ are holes of the pNet.} In this example we use \emph{synchronised actions}, to express actions that cannot be further synchronised, similar to the silent action $\tau$ of CCS.
-We denote them as any action expression with the text underlined, as e.g.
+\ERIC{
+  Consider the pNet $EnableState$ shown in Fig.
+\ref{schema:enable-pnets}, upper part.
+It has two holes $P$ and $Q$, and one PLTS $CState$.
+Note that our graphical syntax presents pNet nodes and synchronisation vectors as finite arrays, where the index sets follow the positions in the arrays.
+  In this example we use \emph{synchronised actions}, to express actions that cannot be further synchronised, similar to the silent action $\tau$ of CCS.
+We denote them as any action expression but with the text underlined, as e.g.
 $\underline{\delta(x_1)}$.
 Such synchronised actions do not play any special role for defining the semantics of pNets, but as one can expect, will be crucial for defining weak equivalences.
-\QIN{The pNet can be given as follow:
+The pNet can be given as follow:
 \begin{itemize}
@@
 	\item[$\bullet$] $J=\{P, Q\}$;
-	\item[$\bullet$] $\symb{SV}=\{\langle a_1, \text{-}, l\rangle\rightarrow a_1[\forall y1.a_1\neq \delta(y1)], 
-	\langle \delta(x_1), acc(x_1), \delta\rangle\rightarrow\underline{\delta(x_1)},\\
-	\langle \text{-}, a_2, r\rangle\rightarrow a_2[\forall y2.a_2\neq acc(y2)]\}$.
+	\item[$\bullet$] $\symb{SV}=$ as listed on the right side of each pNet node.
+        %%   \{\langle a_1, \text{-}, l\rangle\rightarrow a_1[\forall y1.a_1\neq \delta(y1)], 
+	%% \langle \delta(x_1), acc(x_1), \delta\rangle\rightarrow\underline{\delta(x_1)},\\
+	%% \langle \text{-}, a_2, r\rangle\rightarrow a_2[\forall y2.a_2\neq acc(y2)]\}$.
 \end{itemize}
-Replace $CState$ with $CData$ the pNet of $EnableData$ can be given with similar $\symb{SV}$.
+Consider the first  vector of $EnableState$, written as $\langle a_1, \text{-}, l\rangle\rightarrow a_1[\forall y1.
+a_1\neq \delta(y1)]$.
+It denotes a possible behavior of $P>>Q$, for any possible action of the hole $P$ that respects the vector predicate, that is any action that does not match $\delta(y1)$, for any value of the variable $y1$.
+Remark that the data-oriented encoding, in pNet $EnableData$ has the same synchronisation vectors, upto alpha conversion. Only the controller $CState$ has been replaced by $CData$.
 }
@@
 
-Note that synchronisation vectors are defined in a parameterised
-manner:  the first and third lines represent one vector
-for each possible action of hole $P$
-(resp. $Q$). This notation can also use predicates, as in the first
-case, in which we want the vector to apply to any action of $P$
-except for $\delta(z)$.
-
-\QIN{The pNet of $EnableStateCompLeft$ presents a bigger tree with three levels containing a pNet as its node.}
+%% Note that synchronisation vectors are defined in a parameterised
+%% manner:  the first and third lines represent one vector
+%% for each possible action of hole $P$
+%% (resp. $Q$). This notation can also use predicates, as in the first
+%% case, in which we want the vector to apply to any action of $P$
+%% except for $\delta(z)$.
+
+%\QIN{The pNet of $EnableStateCompLeft$ presents a bigger tree with three levels containing a pNet as its node.}
 \begin{example}[pNet of the Composition of ``Enable'' Operators]\label{example:pNetComposeEnable}
-\QIN{
-Consider the encoding $EnableStateCompLeft$ defined in Example \ref{example:ComposeEnableOperators}, the processes $P$, $Q$ and $R$ are holes of the pNet.
-Let $pNet_1$ be the sub-pNet that presents $Q>>R$.
-The pNet can be given as follow:
-\begin{itemize}
-	\item[$\bullet$] $\pNet=\{pNet_1, CState1\}$;
-	\item[$\bullet$] $J=\{P\}$;
-	\item[$\bullet$] $\symb{SV}=\{\langle a_1, \text{-}, l1\rangle\rightarrow a_1[\forall y1.a_1\neq \delta(y1)], 
-	\langle \delta(x_1), acc(x_1), \delta\rangle\rightarrow\underline{\delta(x_1)},\\
-	\langle \text{-}, a_2, r1\rangle\rightarrow a_2[\forall y2.a_2\neq acc(y2)]\}.$
-\end{itemize}
-The sub-pNet $pNet_1$ is a pNet of a single ``Enable'' operator as the pNet in Example \ref{example:pNetEnable}.
+\ERIC{
+  Now consider the pNet $EnableStateCompLeft$ in Fig. \ref{schema:enable-composed}; the processes $P$, $Q$ and $R$ are holes of the pNet.
+It has been obtained by replacing the second hole in pNet $EnableState$ by another pNet representing $Q>>R$.
+Technicaly, the action constants in the PLTS $CState1$ and $CState2$ have been renamed to avoid clashes, and the variables in the vectors also given different names.
+%%   Let $pNet_1$ be the sub-pNet that presents $Q>>R$. The pNet can be given as follow:
+%% \begin{itemize}
+%% 	\item[$\bullet$] $\pNet=\{pNet_1, CState1\}$;
+%% 	\item[$\bullet$] $J=\{P\}$;
+%% 	\item[$\bullet$] $\symb{SV}=\{\langle a_1, \text{-}, l1\rangle\rightarrow a_1[\forall y1.a_1\neq \delta(y1)], 
+%% 	\langle \delta(x_1), acc(x_1), \delta\rangle\rightarrow\underline{\delta(x_1)},\\
+%% 	\langle \text{-}, a_2, r1\rangle\rightarrow a_2[\forall y2.a_2\neq acc(y2)]\}.$
+%% \end{itemize}
+%% The sub-pNet $pNet_1$ is a pNet of a single ``Enable'' operator as the pNet in Example \ref{example:pNetEnable}.
 Actions in $pNet_1$ should be renamed to distinguish themselves from those already used in the pNet of $EnableStateCompLeft$.
@@
 
-In Figures~\ref{schema:enable-pnets},\ref{schema:enable-composed}, we show
-examples of these constructs, with two PLTSs, one hole and one pNet
-node encoding our running example.
+%% In Figures~\ref{schema:enable-pnets},\ref{schema:enable-composed}, we show
+%% examples of these constructs, with two PLTSs, one hole and one pNet
+%% node encoding our running example.
 
@@
 %\label{section:running-example}
-
-\begin{figure}[t]
-\begin{minipage}{6.1cm}
-
-  \includegraphics[width=\linewidth]{ActaXFIG/Enable1}
-  \\[1.3ex]
- \includegraphics[width=\linewidth]{ActaXFIG/Enable2}
-  \caption{Two pNet encodings for  Enable }  \label{schema:enable-pnets}
-\end{minipage}
-  \hspace{2mm}
-\begin{minipage}{6cm}
-  \includegraphics[width=\linewidth]{ActaXFIG/P-QR}
-  \caption{Composed pNet for ``$P>>(Q>>R)$''}  \label{schema:enable-composed}
-\end{minipage}
-
-\end{figure}
 
@@
           \xrightarrow{acc(x2)}_Q \} ~~
-          [v_1=0 \land v_2 = 0 \land \forall z. acc(x2) \neq
-            \delta(z)] ~~ \{v1:=1\}
+          [v_1=0 \land v_2 = 0 \land \forall y1. acc(x2) \neq
+            \delta(y1)] ~~ \{v1:=1\}
         }
@@
           \xrightarrow{acc(x2)}_R \} ~~
-          [a1 = \delta(x2) \land \forall z. a1 \neq \delta(z)]
+          [a1 = \delta(x2) \land \forall y1. a1 \neq \delta(y1)]
         }
@@
 unsatisfiable open transition 
-from the open automaton of our running example.
+from the open automaton of Fig. \ref{schema:enable-composed}.
 It shows the case where processes $P$ and $R$ ``try'' to communicate directly, but this is made impossible by the combination of chosen synchronisation vectors and their guards. This
@@
 where each $Assign$ represents one of the possible (symbolic) values of
- the state variable $v$.
+variable $v$.
+
+\ERIC{Each call to the SMT engine will return either SAT or UNSAT results, or may fail due to time bounds.
+Also, the accuracy of a 'SAT' result may depend on the characteristics of the specific theory used to axiomatise the data domains and operators.
+Such theories may be intrinsically undecidable, or may not properly handled by the SMT engine (e.g.
+for recursive datatypes).
+However, while building the open automaton, that is a symbolic representation of the pNet behavior, it is not logically incorrect to keep potentialy unsatisfiable transitions, so we will treat undecidable results, and time bounds failures, as SAT.
+So the open automaton, may have more transitions and states that the theoretical minimum.}
+
+\ERIC{So this is not a problem in itself when constructing the automaton, but a similar limitation will arise later when using open automata as the input of model checking or equivalence checking algorithms.
+Note that decidability results for these
+will be dependent on the decidability of the SMT theories used, as is proved e.g. in \cite{henrio:Forte2016} for bisimulation.}
 
@@
 
-\subsection{Translation to SMTlib}
+\subsection{Translation to SMTlib and Satisfiability Check}
 \label{section:TranslationToSMTlib}
@@
 
-Figure~\ref{schema:smt-lib} shows the translation of  Figure~\ref{schema:unsat-ot}
+Figure~\ref{schema:smt-lib} shows the translation of  Example~\ref{schema:unsat-ot}, page \pageref{schema:unsat-ot},
 in the SMTlib syntax. It contains the declaration
@@
 
-Here the behavior of the hole ``$P$'' ($a1$ in Figure~\ref{schema:unsat-ot}), after matching with the synchronisation vectors, appears as a variable
+Here the behavior of the hole ``$P$'' ($a1$ in Example~\ref{schema:unsat-ot}), after matching with the synchronisation vectors, appears as a variable
 ``|a1:sva\_SVA0:15:1|'', and ``$R$'' ($acc(x2)$) as ``|(ACT delta

### 2019-11-05 2016-Weak-FH-Bisim/WeakBisim.tex

@@
 
+When silent actions cannot be observed, weak bisimulation is a congruence for open pNets: if $P$ and $Q$ are weakly bisimilar to $P'$ and $Q'$ then the composition of $P$ and $Q$ is weakly bisimilar to the composition of$P'$ and $Q'$, where composition is the hole replacement operator: 	$\pNet[\pNetQ]_{j}$ and
+	$\pNet'[\pNetQ']_{j}$ are weak FH-bisimilar. This can be shown by proving the two following theorems.
+
 \begin{theorem}[Congruence for  weak bisimulation]\label{weak-thm-congr-eq}
@@
 \end{theorem}
+
+The detailed proof of these theorem can be found in~\ref{app-WFH-equiv}.
+The proof strongly relies on the fact that weak FH-bisimulation is an equivalence, but also on the composition properties for open automata.
 

### 2019-11-05 2017-Xudong-SMT/ActaInformatica.tex

@@
   Suppose we have two unspecified processes $P$ and $Q$.
-In the Enable expression ``$P>>Q$'', an \texttt{exit} statement within $P$ terminates the current process and pass the control to $Q$, carrying a value $x$ that is captured by the \texttt{accept} statement of $Q$.
+In the Enable expression ``$P>>Q$'', an \texttt{exit} statement within $P$ terminates the current process and passes the control to $Q$, carrying a value $x$ that is captured by the \texttt{accept} statement of $Q$.
   In the next section we will define pNet encodings of the Enable operator. Let us start by defining the algebra presentation that will be used in these pNets.
@@
 
-\ERIC{The $EnableData$ pNet will use the same algebra presentation.}
+\ERIC{The $EnableData$ pNet will use the same algebra presentation.}\QIN{The main difference between $EnableState$ and $EnableData$ lies in the construction of their controller $CState$ and $CData$ which we will discuss in the next section.}
 %\QIN{
@@
 \end{itemize}
+}
+\QIN{
 Featuring guards and assignments in the label of transitions, the PLTS of the controller $CData$ is $\langle S,s_0, \to\rangle$ where:
 \begin{itemize}
-	\item[$\bullet$] $S=\{0, 1\}$, $s_0=0$, $vars(s_0)=\{v\}$, $\texttt{init}\ \{v:=0\}$;
-	\item[$\bullet$] $\to=\{0\xrightarrow{l, [v=0]}0, 0\xrightarrow{\delta,  [v=0], \{v\leftarrow1\}}1, 1\xrightarrow{r, [v=1]}1\}$.
+	\item[$\bullet$] $S=\{0\}$, $s_0=0$, $vars(s_0)=\{v\}$, $\texttt{init}\ \{v:=0\}$;
+	\item[$\bullet$] $\to=\{0\xrightarrow{l, [v=0]}0, 0\xrightarrow{\delta,  [v=0], \{v\leftarrow1\}}0, 0\xrightarrow{r, [v=1]}0\}$.
 \end{itemize}
@@
 \ERIC{Each call to the SMT engine will return either SAT or UNSAT results, or may fail due to time bounds.
-Also, the accuracy of a 'SAT' result may depend on the characteristics of the specific theory used to axiomatise the data domains and operators.
+Also, the accuracy of a `SAT' result may depend on the characteristics of the specific theory used to axiomatise the data domains and operators.
 Such theories may be intrinsically undecidable, or may not properly handled by the SMT engine (e.g.
 for recursive datatypes).
-However, while building the open automaton, that is a symbolic representation of the pNet behavior, it is not logically incorrect to keep potentialy unsatisfiable transitions, so we will treat undecidable results, and time bounds failures, as SAT.
+However, while building the open automaton, that is a symbolic representation of the pNet behavior, it is not logically incorrect to keep potentially unsatisfiable transitions, so we will treat undecidable results, and time bounds failures, as SAT.
 So the open automaton, may have more transitions and states that the theoretical minimum.}

### 2019-11-06 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf. paper: Add explanation on page 22.
minor changes

@@
 \begin{example}[The ``Enable'' Operator]\label{example:EnableOperator}
-\ERIC{In Fig. \ref{schema:enable-pnets} we shall give two possible pNet  encodings of the ``Enable'' operator respectively state-oriented and data-oriented. 
-The first one is called $EnableState$, and uses a controller $CState$ with three simple control actions $l, r, \delta$ in it to synchronise the behaviour of $P$ and $Q$.
+\ERIC{In Fig. \ref{schema:enable-pnets} we give two possible pNet  encodings of the ``Enable'' operator, \YX{which are  state-oriented and data-oriented, respectively.} 
+The first one is called $EnableState$, and uses a controller $CState$ with three simple control actions, $l, r$ and $\delta$,  to synchronise the behaviour of $P$ and $Q$.
 Here we use a simple action algebra, containing two constructors $\delta(x)$ and $acc(x)$, for any possible data type of the variable $x$, corresponding to the LOTOS statements \texttt{exit} and \texttt{accept}.
-To construct the algebra presentation, we extend the triple $\APres=\langle\mathit{Sorts},\mathit{Constrs},\mathit{Ops}\rangle$ shown in Table \ref{table:BIPalgebra} with four new action constant constructors $l, r, \delta, acc$.}
+To construct the algebra presentation, we extend the triple $\APres=\langle\mathit{Sorts},\mathit{Constrs},\mathit{Ops}\rangle$ shown in Table \ref{table:BIPalgebra} with four new action constant constructors $l, r, \delta$ and $acc$.}
 
@@
 
-\ERIC{The $EnableData$ pNet will use the same algebra presentation.}\QIN{The main difference between $EnableState$ and $EnableData$ lies in the construction of their controller $CState$ and $CData$ which we will discuss in the next section.}
+\ERIC{The $EnableData$ pNet uses the same algebra presentation.}\QIN{The main difference between $EnableState$ and $EnableData$ lies in the construction of their controllers $CState$ and $CData$ that we will discuss in the next section.}
 %\QIN{
@@
 \QIN{
-Featuring guards and assignments in the label of transitions, the PLTS of the controller $CData$ is $\langle S,s_0, \to\rangle$ where:
+%Featuring guards and assignments in the label of transitions, 
+\YX{The PLTS of the controller $CData$ is $\langle S',s'_0, \to\rangle$} where:
 \begin{itemize}
-	\item[$\bullet$] $S=\{0\}$, $s_0=0$, $vars(s_0)=\{v\}$, $\texttt{init}\ \{v:=0\}$;
+	\item[$\bullet$] \YX{$S'=\{0\}$, $s'_0=0$, $vars(s'_0)=\{v\}$;} % $\texttt{init}\ \{v:=0\}$;
 	\item[$\bullet$] $\to=\{0\xrightarrow{l, [v=0]}0, 0\xrightarrow{\delta,  [v=0], \{v\leftarrow1\}}0, 0\xrightarrow{r, [v=1]}0\}$.
@@
   In this example we use \emph{synchronised actions}, to express actions that cannot be further synchronised, similar to the silent action $\tau$ of CCS.
-We denote them as any action expression but with the text underlined, as e.g.
+We denote them as any action expression but with the text underlined,  e.g.
 $\underline{\delta(x_1)}$.
-Such synchronised actions do not play any special role for defining the semantics of pNets, but as one can expect, will be crucial for defining weak equivalences.
+Such synchronised actions do not play any special role for defining the semantics of pNets, but as one can expect, they will be crucial for defining weak equivalences.
 The pNet can be given as follow:
@@
 a_1\neq \delta(y1)]$.
-It denotes a possible behavior of $P>>Q$, for any possible action of the hole $P$ that respects the vector predicate, that is any action that does not match $\delta(y1)$, for any value of the variable $y1$.
-Remark that the data-oriented encoding, in pNet $EnableData$ has the same synchronisation vectors, upto alpha conversion. Only the controller $CState$ has been replaced by $CData$.
+It denotes a possible behavior of $P>>Q$, for any possible action of the hole $P$ that respects the vector predicate, that is, any action that does not match $\delta(y1)$, for any value of the variable $y1$.
+Remark that the data-oriented encoding in pNet $EnableData$ has the same synchronisation vectors, up to the usual alpha conversion. Only the controller $CState$ has been replaced by $CData$.
 }
@@
 \ERIC{
-  Now consider the pNet $EnableStateCompLeft$ in Fig. \ref{schema:enable-composed}; the processes $P$, $Q$ and $R$ are holes of the pNet.
+  Now consider the pNet $EnableStateCompLeft$ in Fig. \ref{schema:enable-composed}; the processes $P$, $Q$ and $R$ are three holes of the pNet.
 It has been obtained by replacing the second hole in pNet $EnableState$ by another pNet representing $Q>>R$.
-Technicaly, the action constants in the PLTS $CState1$ and $CState2$ have been renamed to avoid clashes, and the variables in the vectors also given different names.
+Technically, the action constants in the PLTS $CState1$ and $CState2$ have been renamed to avoid clashes, and the variables in the vectors are also given different names.
 %%   Let $pNet_1$ be the sub-pNet that presents $Q>>R$. The pNet can be given as follow:
@@
 However, while building the open automaton, that is a symbolic representation of the pNet behavior, it is not logically incorrect to keep potentially unsatisfiable transitions, so we will treat undecidable results, and time bounds failures, as SAT.
-So the open automaton, may have more transitions and states that the theoretical minimum.}
-
-\ERIC{So this is not a problem in itself when constructing the automaton, but a similar limitation will arise later when using open automata as the input of model checking or equivalence checking algorithms.
+So the open automaton may have more transitions and states than the theoretical minimum.}
+
+\ERIC{This is not a problem in itself when constructing the automaton, but a similar limitation will arise later when using open automata as the input of model checking or equivalence checking algorithms.
 Note that decidability results for these
-will be dependent on the decidability of the SMT theories used, as is proved e.g. in \cite{henrio:Forte2016} for bisimulation.}
+will be dependent on the decidability of the SMT theories used, as is proved e.g. in \cite{henrio:Forte2016}, for bisimulations.}
 
@@
 
-\QIN{As the removal of the unsatisfiable transitions leads to some transitions losing their pioneer transitions, }
-the set $L1$ may contain unreachable transitions. To remove those transitions, the last step of the  
+\QIN{As the removal of the unsatisfiable transitions \YX{may entail some transitions without proceeding} transitions, }
+the set $L1$ might contain unreachable transitions. To remove those transitions, the last step of the  
 algorithm (lines 12-14) builds the final open automaton via a traversal of $L1$,
@@
 result.
-\QIN{From a  practical point of view, the unreachable transitions is usually a small part of result open transitions, very little will be gained to compute the fixed point.
+\QIN{\YX{Empirically, the unreachable transitions constitute  a small part of the ultimate} open transitions, very little will be gained to compute the fixed point.
 So we would only perform one step of iteration.} Further algorithms
@@
 Figure~\ref{schema:enable-OAs}. 
-\QIN{The initial transition of $EnableData$ is transformed to the initialisation of the state variables, here is $\{v\leftarrow1\}$, for its open automata.}
+\QIN{The initial transition of $EnableData$ is transformed to the initialisation of the state variables, which is $\{v\leftarrow1\}$, for its open automata.}
 Note that although these automata look very similar to the PLTS
@@
 Additional properties are provided in~\cite{Avocs-RR}.
+\YX{Once we have generated the open automaton of the architecture, such properties can be verified by model checking tools, which is beyond the scope of the current work.}
 

### 2019-11-07 2017-Xudong-SMT/ActaInformatica.tex
proofreading and correction of new text...

@@
 	\item to separate clearly the 
-	algorithm 
-	\YX{that generates the transitions of an open automaton from
+	algorithm that generates the transitions of an open automaton from
 	the symbolic reasoning part that uses an SMT
 	engine to check the
-	satisfiability of the predicates generated by the algorithm;}
+	satisfiability of the predicates generated by the algorithm;
 
@@
 Among these works, several have % shown the capability 
-\YX{
-demonstrated the usefulness
-of SMT engines
+demonstrated the usefulness of SMT engines
 (either Z3 or Yikes) as servers for solving verification conditions of
@@
 \cite{DBLP:journals/corr/abs-1806-11459,DBLP:journals/corr/CimattiGMT13}).
-}
 With
@@
 
-\begin{example}[PLTS of the Controller in the ``Enable'' Operator]
+\begin{example}[PLTS of the Controllers in the ``Enable'' Operator]
+
   \ERIC{
 The PLTS of the controller $CState$ from Example \ref{example:EnableOperator} is  $\langle S,s_0, \to\rangle$, where:
-\begin{itemize}
-	\item[$\bullet$] $S=\{0, 1\}$, $s_0=0$;
-	\item[$\bullet$] $\to=\{0\xrightarrow{l}0, 0\xrightarrow{\delta}1, 1\xrightarrow{r}1\}$.
-\end{itemize}
+$$S=\{0, 1\}; s_0=0;
+	 \to=\{0\xrightarrow{l}0, 0\xrightarrow{\delta}1, 1\xrightarrow{r}1\}$$.
 }
@@
 %Featuring guards and assignments in the label of transitions, 
-\YX{The PLTS of the controller $CData$ is $\langle S',s'_0, \to\rangle$} where:
-\begin{itemize}
-	\item[$\bullet$] \YX{$S'=\{0\}$, $s'_0=0$, $vars(s'_0)=\{v\}$;} % $\texttt{init}\ \{v:=0\}$;
-	\item[$\bullet$] $\to=\{0\xrightarrow{l, [v=0]}0, 0\xrightarrow{\delta,  [v=0], \{v\leftarrow1\}}0, 0\xrightarrow{r, [v=1]}0\}$.
-\end{itemize}
-}
+\YX{And the PLTS of the controller $CData$ is $\langle S',s'_0, \to\rangle$} where:
+ \ERIC{$$S'=\{0\}; s'_0=0; vars(0)=\{v\}; \texttt{init}\ \{v:=0\};$$
+	 $$\to=\{0\xrightarrow{l, [v=0]}0, 0\xrightarrow{\delta,  [v=0], \{v:=1\}}0, 0\xrightarrow{r, [v=1]}0\}$$.
+  }}
 \ERIC{The PLTSs contained in $EnableStateCompLeft$ are similar to the PLTS $CState$, but their action constants have been renamed, ensuring disjoint state variable sets.}
@@
 While matching a vector with a combination tuple, \emph{Matching}
-tries to filter out some incompatibilities \QIN{in advance.
-If some of the subnet actions are marked inactive in the vector while some of the behaviours at the corresponding positions in the chosen combination are active, the matching would fail and the algorithm can filter it.}
+tries to filter out some incompatibilities \ERIC{as early as possible.} \QIN{If some of the subnet actions are marked inactive in the vector while some of the behaviours at the corresponding positions in the chosen combination are active, the matching would fail and the algorithm can filter it.}
 
@@
 the predicates express incompatible constraints. 
-\QIN{Such constraints come from the mismatching of the actions by pattern-matching or unification, involving the guards, which are all presented in the predicates.}
+\QIN{Such constraints come from the mismatching of the actions by pattern-matching or unification, \ERIC{including the guards collected from PLTSs and synchronisation vectors}, which are all present in the predicates.}
 Even if having an
@@
 
-\QIN{As the removal of the unsatisfiable transitions \YX{may entail some transitions without proceeding} transitions, }
+\QIN{As the removal of the unsatisfiable transitions \YX{may entail some transitions without preceeding} transitions, }
 the set $L1$ might contain unreachable transitions. To remove those transitions, the last step of the  
@@
 In practice, this could be
-expensive \QIN{as it needs several times of traversal of the whole set of open transitions}, and it is not incorrect to leave some UNSAT OTs in the
+expensive \QIN{as it requires several traversals of the whole set of open transitions}, and it is not incorrect to leave some UNSAT OTs in the
 result.
-\QIN{\YX{Empirically, the unreachable transitions constitute  a small part of the ultimate} open transitions, very little will be gained to compute the fixed point.
+\QIN{\YX{Empirically, on real life systems, the unreachable transitions constitute  a small part of the ultimate} open transitions, very little will be gained to compute the fixed point.
 So we would only perform one step of iteration.} Further algorithms
@@
 Figure~\ref{schema:enable-OAs}. 
-\QIN{The initial transition of $EnableData$ is transformed to the initialisation of the state variables, which is $\{v\leftarrow1\}$, for its open automata.}
+\QIN{The initial transition of $EnableData$ is transformed to the initialisation of the state variables, which is $\{v\leftarrow 0\}$, for its open automata.}
 Note that although these automata look very similar to the PLTS

### 2019-11-08 2017-Xudong-SMT/ActaInformatica.tex
page 21, + bibref + reviews,docx

@@
 We have shown in \cite{henrio:Forte2016} 
-\YX{that the two open automata are equivalent with respect to a notion of FH-bisimulation.}
+\YX{that the two open automata are equivalent with respect to a notion of (symbolic) FH-bisimulation.}
 %how to prove that they are bisimilar.
@@
 
-Figure~\ref{schema:ArchFailure:BIP} shows a refined version of the
+\ERIC{The original specification of the nanosatellite software, using BIP architecture patterns, was handling data in the BIP components behavior, but was not able to use data in the synchronisation between components.
+We have shown in \cite{BHM19:Coordination} how to overcome this limit, allowing data constraints in BIP architecture connectors, and providing an encoding of such architectures in terms of open pNets.}
+
+Figure~\ref{schema:ArchFailure:BIP} shows this refined version of the
 Failure Monitor architecture used in~\cite{CubETH-case-study}.

### 2019-11-08 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf. paper: Improve fig1,2 and corresponding variables.
Main: Figure 1 and Figure 2
Example 3, 3rd paragraph: y1 -> y_1
Example 5, figure: y1 -> y_1, x2 -> x_2, v1 -> v_1
Example 6, figure: y1 -> y_1, x2 -> x_2, a1 -> a_1
Figure 4: y1 -> y_1, y2 -> y_2

--- 2019-11-06 2017-Xudong-SMT/ActaInformatica.tex
@@
 \begin{example}[The ``Enable'' Operator]\label{example:EnableOperator}
-\ERIC{In Fig. \ref{schema:enable-pnets} we give two possible pNet  encodings of the ``Enable'' operator, \YX{which are  state-oriented and data-oriented, respectively.} 
-The first one is called $EnableState$, and uses a controller $CState$ with three simple control actions, $l, r$ and $\delta$,  to synchronise the behaviour of $P$ and $Q$.
+\ERIC{In Fig. \ref{schema:enable-pnets} we shall give two possible pNet  encodings of the ``Enable'' operator respectively state-oriented and data-oriented. 
+The first one is called $EnableState$, and uses a controller $CState$ with three simple control actions $l, r, \delta$ in it to synchronise the behaviour of $P$ and $Q$.
 Here we use a simple action algebra, containing two constructors $\delta(x)$ and $acc(x)$, for any possible data type of the variable $x$, corresponding to the LOTOS statements \texttt{exit} and \texttt{accept}.
-To construct the algebra presentation, we extend the triple $\APres=\langle\mathit{Sorts},\mathit{Constrs},\mathit{Ops}\rangle$ shown in Table \ref{table:BIPalgebra} with four new action constant constructors $l, r, \delta$ and $acc$.}
+To construct the algebra presentation, we extend the triple $\APres=\langle\mathit{Sorts},\mathit{Constrs},\mathit{Ops}\rangle$ shown in Table \ref{table:BIPalgebra} with four new action constant constructors $l, r, \delta, acc$.}
 
@@
 
-\ERIC{The $EnableData$ pNet uses the same algebra presentation.}\QIN{The main difference between $EnableState$ and $EnableData$ lies in the construction of their controllers $CState$ and $CData$ that we will discuss in the next section.}
+\ERIC{The $EnableData$ pNet will use the same algebra presentation.}\QIN{The main difference between $EnableState$ and $EnableData$ lies in the construction of their controller $CState$ and $CData$ which we will discuss in the next section.}
 %\QIN{
@@
 \QIN{
-%Featuring guards and assignments in the label of transitions, 
-\YX{The PLTS of the controller $CData$ is $\langle S',s'_0, \to\rangle$} where:
+Featuring guards and assignments in the label of transitions, the PLTS of the controller $CData$ is $\langle S,s_0, \to\rangle$ where:
 \begin{itemize}
-	\item[$\bullet$] \YX{$S'=\{0\}$, $s'_0=0$, $vars(s'_0)=\{v\}$;} % $\texttt{init}\ \{v:=0\}$;
+	\item[$\bullet$] $S=\{0\}$, $s_0=0$, $vars(s_0)=\{v\}$, $\texttt{init}\ \{v:=0\}$;
 	\item[$\bullet$] $\to=\{0\xrightarrow{l, [v=0]}0, 0\xrightarrow{\delta,  [v=0], \{v\leftarrow1\}}0, 0\xrightarrow{r, [v=1]}0\}$.
@@
   In this example we use \emph{synchronised actions}, to express actions that cannot be further synchronised, similar to the silent action $\tau$ of CCS.
-We denote them as any action expression but with the text underlined,  e.g.
+We denote them as any action expression but with the text underlined, as e.g.
 $\underline{\delta(x_1)}$.
-Such synchronised actions do not play any special role for defining the semantics of pNets, but as one can expect, they will be crucial for defining weak equivalences.
+Such synchronised actions do not play any special role for defining the semantics of pNets, but as one can expect, will be crucial for defining weak equivalences.
 The pNet can be given as follow:
@@
 \end{itemize}
-Consider the first  vector of $EnableState$, written as $\langle a_1, \text{-}, l\rangle\rightarrow a_1[\forall y1.
-a_1\neq \delta(y1)]$.
-It denotes a possible behavior of $P>>Q$, for any possible action of the hole $P$ that respects the vector predicate, that is, any action that does not match $\delta(y1)$, for any value of the variable $y1$.
-Remark that the data-oriented encoding in pNet $EnableData$ has the same synchronisation vectors, up to the usual alpha conversion. Only the controller $CState$ has been replaced by $CData$.
+Consider the first  vector of $EnableState$, written as $\langle a_1, \text{-}, l\rangle\rightarrow a_1[\forall y_1.
+a_1\neq \delta(y_1)]$.
+It denotes a possible behavior of $P>>Q$, for any possible action of the hole $P$ that respects the vector predicate, that is any action that does not match $\delta(y_1)$, for any value of the variable $y_1$.
+Remark that the data-oriented encoding, in pNet $EnableData$ has the same synchronisation vectors, up to alpha conversion. Only the controller $CState$ has been replaced by $CData$.
 }
@@
 \ERIC{
-  Now consider the pNet $EnableStateCompLeft$ in Fig. \ref{schema:enable-composed}; the processes $P$, $Q$ and $R$ are three holes of the pNet.
+  Now consider the pNet $EnableStateCompLeft$ in Fig. \ref{schema:enable-composed}; the processes $P$, $Q$ and $R$ are holes of the pNet.
 It has been obtained by replacing the second hole in pNet $EnableState$ by another pNet representing $Q>>R$.
-Technically, the action constants in the PLTS $CState1$ and $CState2$ have been renamed to avoid clashes, and the variables in the vectors are also given different names.
+Technically, the action constants in the PLTS $CState1$ and $CState2$ have been renamed to avoid clashes, and the variables in the vectors also given different names.
 %%   Let $pNet_1$ be the sub-pNet that presents $Q>>R$. The pNet can be given as follow:
@@
           \inferrule*[myfraction=\reddottedrule]
-	{\{\xrightarrow{\delta(x2)}_P ~~
-          \xrightarrow{acc(x2)}_Q \} ~~
-          [\forall y1. acc(x2) \neq \delta(y1)]
+	{\{\xrightarrow{\delta(x_2)}_P ~~
+          \xrightarrow{acc(x_2)}_Q \} ~~
+          [\forall y_1. acc(x_2) \neq \delta(y_1)]
         }
-	{\ostate{0,0} \xrightarrow {\underline{\delta(x2)}} \ostate{1,0}}
+	{\ostate{0,0} \xrightarrow {\underline{\delta(x_2)}} \ostate{1,0}}
 	\end{mathpar}
@@
           \inferrule*[myfraction=\reddottedrule]
-	{\{\xrightarrow{\delta(x2)}_P ~~
-          \xrightarrow{acc(x2)}_Q \} ~~
-          [v_1=0 \land v_2 = 0 \land \forall y1. acc(x2) \neq
-            \delta(y1)] ~~ \{v1:=1\}
+	{\{\xrightarrow{\delta(x_2)}_P ~~
+          \xrightarrow{acc(x_2)}_Q \} ~~
+          [v_1=0 \land v_2 = 0 \land \forall y_1. acc(x_2) \neq
+            \delta(y_1)] ~~ \{v_1:=1\}
         }
-	{\ostate{0,0} \xrightarrow {\underline{\delta(x2)}} \ostate{0,0}}
+	{\ostate{0,0} \xrightarrow {\underline{\delta(x_2)}} \ostate{0,0}}
 	\end{mathpar}
@@
           \inferrule*[myfraction=\reddottedrule]
-	{\{\xrightarrow{a1}_P ~~
-          \xrightarrow{acc(x2)}_R \} ~~
-          [a1 = \delta(x2) \land \forall y1. a1 \neq \delta(y1)]
+	{\{\xrightarrow{a_1}_P ~~
+          \xrightarrow{acc(x_2)}_R \} ~~
+          [a_1 = \delta(x_2) \land \forall y_1. a_1 \neq \delta(y_1)]
         }
-	{\ostate{2,0} \xrightarrow {\underline{\delta(x2)}} \ostate{3,0}}
+	{\ostate{2,0} \xrightarrow {\underline{\delta(x_2)}} \ostate{3,0}}
 	\end{mathpar}
@@
   mismatch is materialised by the predicate
-fragment ``$a1 = \delta(x2) \land \forall z. a1 \neq \delta(z)$''. In Section~\ref{section:TranslationToSMTlib} we will show how this is encoded and checked using the SMT engine.
+fragment ``$a_1 = \delta(x_2) \land \forall z. a_1 \neq \delta(z)$''. In Section~\ref{section:TranslationToSMTlib} we will show how this is encoded and checked using the SMT engine.
 \end{example}
@@
 However, while building the open automaton, that is a symbolic representation of the pNet behavior, it is not logically incorrect to keep potentially unsatisfiable transitions, so we will treat undecidable results, and time bounds failures, as SAT.
-So the open automaton may have more transitions and states than the theoretical minimum.}
-
-\ERIC{This is not a problem in itself when constructing the automaton, but a similar limitation will arise later when using open automata as the input of model checking or equivalence checking algorithms.
+So the open automaton, may have more transitions and states that the theoretical minimum.}
+
+\ERIC{So this is not a problem in itself when constructing the automaton, but a similar limitation will arise later when using open automata as the input of model checking or equivalence checking algorithms.
 Note that decidability results for these
-will be dependent on the decidability of the SMT theories used, as is proved e.g. in \cite{henrio:Forte2016}, for bisimulations.}
+will be dependent on the decidability of the SMT theories used, as is proved e.g. in \cite{henrio:Forte2016} for bisimulation.}
 
@@
 
-\QIN{As the removal of the unsatisfiable transitions \YX{may entail some transitions without proceeding} transitions, }
-the set $L1$ might contain unreachable transitions. To remove those transitions, the last step of the  
+\QIN{As the removal of the unsatisfiable transitions leads to some transitions losing their pioneer transitions, }
+the set $L1$ may contain unreachable transitions. To remove those transitions, the last step of the  
 algorithm (lines 12-14) builds the final open automaton via a traversal of $L1$,
@@
 result.
-\QIN{\YX{Empirically, the unreachable transitions constitute  a small part of the ultimate} open transitions, very little will be gained to compute the fixed point.
+\QIN{From a  practical point of view, the unreachable transitions is usually a small part of result open transitions, very little will be gained to compute the fixed point.
 So we would only perform one step of iteration.} Further algorithms
@@
 $  \begin{array}{@{}r@{}l@{}}
-    ot_1  = &\openrule{\{ \xrightarrow{a_1}_P \},\\ [\forall y1. a_1\neq\delta(y1)]}
+    ot_1  = &\openrule{\{ \xrightarrow{a_1}_P \},\\ [\forall y_1. a_1\neq\delta(y_1)]}
     {A_0 \xrightarrow{a_1} A_0}\\
@@
     ot_3  =& \openrule{
-                          \{  \xrightarrow{a_2}_Q \},\\ [\forall y2. a_2\neq acc(y2)] }
+                          \{  \xrightarrow{a_2}_Q \},\\ [\forall y_2. a_2\neq acc(y_2)] }
     {A_1 \xrightarrow{a_2} A_1}
@@
     ot'_1  =& \openrule{
-    	\{\xrightarrow{b_1}_P\}, ~~ [\forall y1. b_1\neq\delta(y1) \!\land\! v=0]}
+    	\{\xrightarrow{b_1}_P\}, ~~ [\forall y_1. b_1\neq\delta(y_1) \!\land\! v=0]}
     {B_0 \xrightarrow{b_1} B_0}\\
@@
     ot'_3  =& \openrule{
-                            \{\xrightarrow{b_2}_Q\}, ~~ [\forall y2. b_2\neq acc(y2) \!\land\! v=1] }
+                            \{\xrightarrow{b_2}_Q\}, ~~ [\forall y_2. b_2\neq acc(y_2) \!\land\! v=1] }
     {B_1 \xrightarrow{b_2} B_1}
@@
 Figure~\ref{schema:enable-OAs}. 
-\QIN{The initial transition of $EnableData$ is transformed to the initialisation of the state variables, which is $\{v\leftarrow1\}$, for its open automata.}
+\QIN{The initial transition of $EnableData$ is transformed to the initialisation of the state variables, here is $\{v\leftarrow1\}$, for its open automata.}
 Note that although these automata look very similar to the PLTS
@@
 Additional properties are provided in~\cite{Avocs-RR}.
-\YX{Once we have generated the open automaton of the architecture, such properties can be verified by model checking tools, which is beyond the scope of the current work.}
+\QIN{After we generating the open automaton of the architecture, we can check such properties through model checking.
+Here we show its pNet encoding and open automaton.}
 
@@
 In \cite{henrio:Forte2016} this last part is defined as:
-\[\MkPred(SV_k, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow
-\begin{array}{l}
-\exists {(a'_i)}^{i\in I},
-{(b'_j)}^{j\in J},v'.\, SV_k={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v'
-\\~~\land
-\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v'
-\end{array}\]
+\[\MkPred(SV_k, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow SV_k={(a_i)}^{i\in I}, {(b_j)}^{j\in J}\rightarrow v\]
+%\begin{array}{l}
+%\exists {(a'_i)}^{i\in I},
+%{(b'_j)}^{j\in J},v'.\, SV_k={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v'
+%\\~~\land
+%\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v'
+%\end{array}\]
 

### 2019-11-08 2017-Xudong-SMT/ActaInformatica.tex

--- 2019-11-08 2017-Xudong-SMT/ActaInformatica.tex
@@
 \end{itemize}
-Consider the first  vector of $EnableState$, written as $\langle a_1, \text{-}, l\rangle\rightarrow a_1[\forall y1.
-a_1\neq \delta(y1)]$.
+Consider the first  vector of $EnableState$, written as $\langle a_1, \text{-}, l\rangle\rightarrow a_1[\forall y_1.
+a_1\neq \delta(y_1)]$.
 It denotes a possible behavior of $P>>Q$, for any possible action of the hole $P$ that respects the vector predicate, that is, any action that does not match $\delta(y1)$, for any value of the variable $y1$.

### 2019-11-11 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf. paper: Add more explanation on page 5.

@@
 On top of $\mathcal{E}_\P$ we build the action algebra
-$\mathcal{A}_\P$, with $\mathcal{A}_\P\subseteq\mathcal{T}_\P \wedge
-\mathcal{E}_\P\cap\mathcal{A}_\P=\emptyset$;
+$\mathcal{A}_\P$, with $\mathcal{A}_\P\subseteq\mathcal{T}_\P$.
+\QIN{As action expressions $\mathcal{A}_\P$ we built will not be used to present data terms, we have} 
+$\mathcal{E}_\P\cap\mathcal{A}_\P=\emptyset$;
  action terms will use data expressions as sub-terms.
@@
 $$S=\{0, 1\}; s_0=0;
-	 \to=\{0\xrightarrow{l}0, 0\xrightarrow{\delta}1, 1\xrightarrow{r}1\}$$.
+	 \to=\{0\xrightarrow{l}0, 0\xrightarrow{\delta}1, 1\xrightarrow{r}1\}.$$
 }
@@
  \ERIC{$$S'=\{0\}; s'_0=0; vars(0)=\{v\}; \texttt{init}\ \{v:=0\};$$
-	 $$\to=\{0\xrightarrow{l, [v=0]}0, 0\xrightarrow{\delta,  [v=0], \{v:=1\}}0, 0\xrightarrow{r, [v=1]}0\}$$.
+	 $$\to=\{0\xrightarrow{l, [v=0]}0, 0\xrightarrow{\delta,  [v=0], \{v:=1\}}0, 0\xrightarrow{r, [v=1]}0\}.$$
   }}
@@
     ot'_2  =& \openrule{
-                            \{\xrightarrow{\delta(y_2)}_P,\,
+                            \{\xrightarrow{\delta(x_2)}_P,\,
                             \xrightarrow{acc(x_2)}_Q \},~

### 2019-11-11 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf. paper: Typos as variables in Fig. 1,2 improved.

@@
 a_1\neq \delta(y_1)]$.
-It denotes a possible behavior of $P>>Q$, for any possible action of the hole $P$ that respects the vector predicate, that is, any action that does not match $\delta(y1)$, for any value of the variable $y1$.
+It denotes a possible behavior of $P>>Q$, for any possible action of the hole $P$ that respects the vector predicate, that is, any action that does not match $\delta(y_1)$, for any value of the variable $y_1$.
 Remark that the data-oriented encoding in pNet $EnableData$ has the same synchronisation vectors, up to the usual alpha conversion. Only the controller $CState$ has been replaced by $CData$.
@@
 
-Here the behavior of the hole ``$P$'' ($a1$ in Example~\ref{schema:unsat-ot}), after matching with the synchronisation vectors, appears as a variable
-``|a1:sva\_SVA0:15:1|'', and ``$R$'' ($acc(x2)$) as ``|(ACT delta
-|x:sva\_SV4:1:2|''. Line 16 requires that $a1 = \delta(x2)$ to match
+Here the behavior of the hole ``$P$'' ($a_1$ in Example~\ref{schema:unsat-ot}), after matching with the synchronisation vectors, appears as a variable
+``|a1:sva\_SVA0:15:1|'', and ``$R$'' ($acc(x_2)$) as ``|(ACT delta
+|x:sva\_SV4:1:2|''. Line 16 requires that $a_1 = \delta(x_2)$ to match
 the second synchronisation vector of the root pNet node, and lines
-17-18 that $a1$ does not match $\delta(x1)$ for any $x1$. 
+17-18 that $a_1$ does not match $\delta(x_1)$ for any $x_1$. 
 We also display  the diagnosis (``SAT'' or ``UNSAT'') generated by Z3.

### 2019-11-13 2016-Weak-FH-Bisim/WeakBisim.tex
More on Figure 2...
Figs de l'annexe D
traces execution

@@
 the full system should be equivalent (e.g. through weak bisimulation)
-to the two processes connected simply through a perfect medium. Fig. \ref{SimpleProt:Spec}, right, shows the pNet representing this global specification.
+to the two processes connected simply through a perfect medium.
 
@@
 \begin{figure}[t]
-  \centerline{\includegraphics[width=12cm]{XFIG/SimpleProt2-pNet}}
+  \centerline{\includegraphics[width=12cm]{XFIG/SimpleProt2-pNet-tau}}
   \caption{Composed pNet with the Simple Protocol Implementation}  \label{SimpleProt:Impl}
@@
 an expression. More formally, let $\Post$ be any substitution and
-$\Pred$ any predicate suppose $\vars(t)\cap \dom(\Post)=\emptyset$ and
+$\Pred$ any predicate; suppose $\vars(t)\cap \dom(\Post)=\emptyset$ and
 $\vars(t')\cap \dom(\Post)=\emptyset$. Then we have the following
@@
 flexible matching 
-between open transition, to accommodate comparisons between pNet
+between open transitions, to accommodate comparisons between pNet
 expressions with different architectures.
 
-We define now a bisimulaiton relation adapted to open automata and their parametric nature.
+We define now a bisimulation relation adapted to open automata and their parametric nature.
 The relation relates states of the open automaton and states equivalence between the open transitions between the states.
@@
  We name it FH-bisimulation,
- as a short cut for the ``Formal Hypotheses'' manipulated in the
+ as a short cut for the ``Formal Hypotheses'' over the holes behavior manipulated in the
  transitions, but also as a reference to the work of De Simone~\cite{deSimone85},
@@
       if $\Pred_{s,t}$       is 
-      t\\True, i.e. the states are related when the variables in $s$ and $t$ verify the 
+      \\True, i.e. the states are related when the variables in $s$ and $t$ verify the 
       predicate $\Pred_{s,t}$.
@@
 \begin{figure}[t]
-  \centerline{\includegraphics[width=12cm]{XFIG/SimpleProt-pNet}}
+  \centerline{\includegraphics[width=12cm]{XFIG/SimpleProt2-pNet}}
   \caption{Composed pNet with the Simple Protocol Implementation}  \label{App:SimpleProt:Impl}
@@
 
-The corresponding generated Open Automaton was given in Figure \ref{},
-page \pageref{}.
+The corresponding generated Open Automaton was given in Figure \ref{SimpleProtCounter:SpecOA},
+page \pageref{SimpleProtCounter:SpecOA}.
 
@@
 SV11 SVs: <_, _tau_, _>-->_tau_
-SV12 SVs: <_, _tau_, _>-->_tau_
-SV13 SVs: <_, _tau_, _>-->_tau_
-SV14 SVs: <_, _tau_, _>-->_tau_
-SV15 SVs: <_, _tau_, _>-->_tau_
 Holes: P
@@
 
-Finaly, we list here, in raw format, the 24 OTs computed by the tool:
+Finaly, we list here, in raw format, the 12 OTs computed by the tool:
 
 \begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
-INFO  SimpleProtImpl2 - Total: 24 OTs
 INFO  SimpleProtImpl2 - 
-		{P|->p_send(m:sva_SV6:1:1)},   [((in(msg))=:ra:Sender:121:1)/\(:ra:Sender:121:1=(in(m:sva_SV0:12:1)))/\((in(m:sva_SV0:12:1))=(in(m:sva_SV6:1:1)))],   {s1_msg := msg, s1_c := 0}
+	{P|->p_send(m:sva_SV6:1:1)},
+	[(msg=m:sva_SV6:1:1)/\((in(msg))=(in(m:sva_SV6:1:1)))],
+	{s1_msg := msg, s1_c := 0}
 OT:1 ------------------------------------------------------------
@@
 INFO  SimpleProtImpl2 - 
-		{P|->p_a:sva_SV7:1:2},   [(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
+	{P|->p_a:sva_SV7:1:2},
+	[(forall:m:sva_SV7:1:2.
+          (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
 OT:2 ------------------------------------------------------------
@@
 INFO  SimpleProtImpl2 - 
-		{Q|->q_a:sva_SV9:1:4},   [(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
+	{Q|->q_a:sva_SV9:1:4},
+	[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4.
+          (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
 OT:3 ------------------------------------------------------------
@@
 INFO  SimpleProtImpl2 - 
-		{P|->p_a:sva_SV7:1:2},   [(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
+	{P|->p_a:sva_SV7:1:2},
+	[(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
 OT:4 ------------------------------------------------------------
@@
 INFO  SimpleProtImpl2 - 
-		{Q|->q_a:sva_SV9:1:4},   [(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
+	{Q|->q_a:sva_SV9:1:4},
+	[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4.
+          (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
 OT:5 ------------------------------------------------------------
@@
 INFO  SimpleProtImpl2 - 
-		{},   [((s_send(s1_msg, s1_c))=:ra:Sender:1144:1)/\(:ra:Sender:1144:1=(s_send(m:sva_SV1:114:2, c:sva_SV1:114:2)))/\((m_recv(msg, c))=:ra:M1:1145:1)/\(:ra:M1:1145:1=(m_recv(m:sva_SV1:114:2, c:sva_SV1:114:2)))/\(_tau_=_tau_)],   {a1_msg := msg, a1_c := c}
+	{},   [(s1_msg=m:sva_SV1:114:2)/\(s1_c=c:sva_SV1:114:2)
+	  /\((s_send(s1_msg, s1_c))=(s_send(m:sva_SV1:114:2, c:sva_SV1:114:2)))
+          /\(msg=m:sva_SV1:114:2)/\(c=c:sva_SV1:114:2)
+          /\((m_recv(msg, c))=(m_recv(m:sva_SV1:114:2, c:sva_SV1:114:2)))],
+	{a1_msg := msg, a1_c := c}
 OT:6 ------------------------------------------------------------
@@
 INFO  SimpleProtImpl2 - 
-		{},   [((s_send(s1_msg, s1_c))=:ra:Sender:1174:1)/\(:ra:Sender:1174:1=(s_send(m:sva_SV1:117:2, c:sva_SV1:117:2)))/\((m_recv(msg, c))=:ra:M1:1175:1)/\(:ra:M1:1175:1=(m_recv(m:sva_SV1:117:2, c:sva_SV1:117:2)))/\(_tau_=_tau_)],   {a1_msg := msg, a1_c := c}
+	{P|->p_a:sva_SV7:1:2},
+	[(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
 OT:7 ------------------------------------------------------------
-		<s1_a0_r0>-----_tau_----><s2_a1_r0>
+	<s2_a1_r0>-----p_a:sva_SV7:1:2----><s2_a1_r0>
 
 INFO  SimpleProtImpl2 - 
-		{},   [((s_send(s1_msg, s1_c))=:ra:Sender:1204:1)/\(:ra:Sender:1204:1=(s_send(m:sva_SV1:120:2, c:sva_SV1:120:2)))/\((m_recv(msg, c))=:ra:M1:1205:1)/\(:ra:M1:1205:1=(m_recv(m:sva_SV1:120:2, c:sva_SV1:120:2)))/\(_tau_=_tau_)],   {a1_msg := msg, a1_c := c}
+	{Q|->q_a:sva_SV9:1:4},
+	[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4.
+          (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
 OT:8 ------------------------------------------------------------
-		<s1_a0_r0>-----_tau_----><s2_a1_r0>
+	<s2_a1_r0>-----q_a:sva_SV9:1:4----><s2_a1_r0>
 
 INFO  SimpleProtImpl2 - 
-		{},   [((s_send(s1_msg, s1_c))=:ra:Sender:1234:1)/\(:ra:Sender:1234:1=(s_send(m:sva_SV1:123:2, c:sva_SV1:123:2)))/\((m_recv(msg, c))=:ra:M1:1235:1)/\(:ra:M1:1235:1=(m_recv(m:sva_SV1:123:2, c:sva_SV1:123:2)))/\(_tau_=_tau_)],   {a1_msg := msg, a1_c := c}
-	OT:9 ------------------------------------------------------------
-		<s1_a0_r0>-----_tau_----><s2_a1_r0>
+	{},   [],   {}
+OT:9 ------------------------
+	<s2_a1_r0>-----_tau_----><s2_a2_r0>
 
 INFO  SimpleProtImpl2 - 
-		{},   [((s_send(s1_msg, s1_c))=:ra:Sender:1264:1)/\(:ra:Sender:1264:1=(s_send(m:sva_SV1:126:2, c:sva_SV1:126:2)))/\((m_recv(msg, c))=:ra:M1:1265:1)/\(:ra:M1:1265:1=(m_recv(m:sva_SV1:126:2, c:sva_SV1:126:2)))/\(_tau_=_tau_)],   {a1_msg := msg, a1_c := c}
+	{P|->p_a:sva_SV7:1:2},
+	[(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
 OT:10 ------------------------------------------------------------
-		<s1_a0_r0>-----_tau_----><s2_a1_r0>
+	<s2_a2_r0>-----p_a:sva_SV7:1:2----><s2_a2_r0>
 
 INFO  SimpleProtImpl2 - 
-		{P|->p_a:sva_SV7:1:2},   [(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
+	{Q|->q_a:sva_SV9:1:4},
+	[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4.
+          (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
 OT:11 ------------------------------------------------------------
-		<s2_a1_r0>-----p_a:sva_SV7:1:2----><s2_a1_r0>
+	<s2_a2_r0>-----q_a:sva_SV9:1:4----><s2_a2_r0>
 
 INFO  SimpleProtImpl2 - 
-		{Q|->q_a:sva_SV9:1:4},   [(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
-	OT:12 ------------------------------------------------------------
-		<s2_a1_r0>-----q_a:sva_SV9:1:4----><s2_a1_r0>
-
-INFO  SimpleProtImpl2 - 
-		{},   [(_tau_=:ra:M1:11420:1)/\(:ra:M1:11420:1=_tau_)/\(_tau_=_tau_)],   {}
-	OT:13 ------------------------------------------------------------
-		<s2_a1_r0>-----_tau_----><s2_a2_r0>
-
-INFO  SimpleProtImpl2 - 
-		{},   [(_tau_=:ra:M1:11720:1)/\(:ra:M1:11720:1=_tau_)/\(_tau_=_tau_)],   {}
-	OT:14 ------------------------------------------------------------
-		<s2_a1_r0>-----_tau_----><s2_a2_r0>
-
-INFO  SimpleProtImpl2 - 
-		{},   [(_tau_=:ra:M1:12020:1)/\(:ra:M1:12020:1=_tau_)/\(_tau_=_tau_)],   {}
-	OT:15 ------------------------------------------------------------
-		<s2_a1_r0>-----_tau_----><s2_a2_r0>
-
-INFO  SimpleProtImpl2 - 
-		{},   [(_tau_=:ra:M1:12320:1)/\(:ra:M1:12320:1=_tau_)/\(_tau_=_tau_)],   {}
-	OT:16 ------------------------------------------------------------
-		<s2_a1_r0>-----_tau_----><s2_a2_r0>
-
-INFO  SimpleProtImpl2 - 
-		{},   [(_tau_=:ra:M1:12620:1)/\(:ra:M1:12620:1=_tau_)/\(_tau_=_tau_)],   {}
-	OT:17 ------------------------------------------------------------
-		<s2_a1_r0>-----_tau_----><s2_a2_r0>
-
-INFO  SimpleProtImpl2 - 
-		{P|->p_a:sva_SV7:1:2},   [(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
-	OT:18 ------------------------------------------------------------
-		<s2_a2_r0>-----p_a:sva_SV7:1:2----><s2_a2_r0>
-
-INFO  SimpleProtImpl2 - 
-		{Q|->q_a:sva_SV9:1:4},   [(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
-	OT:19 ------------------------------------------------------------
-		<s2_a2_r0>-----q_a:sva_SV9:1:4----><s2_a2_r0>
-
-INFO  SimpleProtImpl2 - 
-		{},   [(s_error=:ra:Sender:11413:1)/\(:ra:Sender:11413:1=s_error)/\(m_error=:ra:M1:11414:1)/\(:ra:M1:11414:1=m_error)/\(_tau_=_tau_)],   {s1_c := s2_c+1}
-	OT:20 ------------------------------------------------------------
+	{},   [],   {s1_c := s2_c+1}
+OT:12 --------------------------------------
 	<s2_a2_r0>-----_tau_----><s1_a0_r0>
 
-INFO  SimpleProtImpl2 - 
-		{},   [(s_error=:ra:Sender:11713:1)/\(:ra:Sender:11713:1=s_error)/\(m_error=:ra:M1:11714:1)/\(:ra:M1:11714:1=m_error)/\(_tau_=_tau_)],   {s1_c := s2_c+1}
-	OT:21 ------------------------------------------------------------
-		<s2_a2_r0>-----_tau_----><s1_a0_r0>
-
-INFO  SimpleProtImpl2 - 
-		{},   [(s_error=:ra:Sender:12013:1)/\(:ra:Sender:12013:1=s_error)/\(m_error=:ra:M1:12014:1)/\(:ra:M1:12014:1=m_error)/\(_tau_=_tau_)],   {s1_c := s2_c+1}
-	OT:22 ------------------------------------------------------------
-		<s2_a2_r0>-----_tau_----><s1_a0_r0>
-
-INFO  SimpleProtImpl2 - 
-		{},   [(s_error=:ra:Sender:12313:1)/\(:ra:Sender:12313:1=s_error)/\(m_error=:ra:M1:12314:1)/\(:ra:M1:12314:1=m_error)/\(_tau_=_tau_)],   {s1_c := s2_c+1}
-	OT:23 ------------------------------------------------------------
-		<s2_a2_r0>-----_tau_----><s1_a0_r0>
-
-INFO  SimpleProtImpl2 - 
-		{},   [(s_error=:ra:Sender:12613:1)/\(:ra:Sender:12613:1=s_error)/\(m_error=:ra:M1:12614:1)/\(:ra:M1:12614:1=m_error)/\(_tau_=_tau_)],   {s1_c := s2_c+1}
-	OT:24 ------------------------------------------------------------
-		<s2_a2_r0>-----_tau_----><s1_a0_r0>
-
-INFO  SimpleProtImpl2 - Total: 24 SATISFIABLE OTs
-INFO  SimpleProtImpl2 -        278 UNSATISFIABLE OTs
-INFO  SimpleProtImpl2 - Total Time: 1056 ms
+INFO   SimpleProtImpl2 - State variables:
+
+Global State: <s0_a0_r0>
+===================
+pLTS States: <s0 vars: {}> <a0 vars: {}> <r0 vars: {}>
+
+Global State: <s1_a0_r0>
+===================
+pLTS States: <s1 vars: { s1_c <-{0, s2_c+1, } s1_msg <-{msg, }}> <a0 vars: {}> <r0 vars: {}>
+
+Global State: <s2_a1_r0>
+===================
+pLTS States: <s2 vars: {}> <a1 vars: { a1_msg <-{msg, } a1_c <-{c, }}> <r0 vars: {}>
+
+Global State: <s2_a2_r0>
+===================
+pLTS States: <s2 vars: {}> <a2 vars: {}> <r0 vars: {}>
+
+INFO  SimpleProtImpl2 - Total: 12 SATISFIABLE OTs
+INFO  SimpleProtImpl2 -        122 UNSATISFIABLE OTs
+INFO  SimpleProtImpl2 - Total Time: 657 ms
 
@@
 \centerline{i;B == B}
-
-\newpage
-  \section{Running example: Hierarchical Broadcast}
-
-Hierarchical Broadcast (HB) is a way of implementing broadcasting
-algorithms within a large set of processes, with better performances
-and scalability. There have been many proposals for hierarchical
-broadcast algorithms (cite...), most of them focussing on specific
-architectures or features (in particular fault tolerance), and on
-performance analysis. Very few have given a formal description of the
-algorithm, allowing to reason about their safety properties.
-In this paper, we choose HB as a running example because it is a
-complex interaction pattern on which the topology and the
-parameterised nature plays a crucial role.
-
-We give here the description of one simple HB algorithm, inspired
-from\cite{Taguchi03}. For the formal description, we define a
-pNet template, that can be used as a building node in a hierarchical
-assembly of processes, organised in a tree of sub-groups. Inside each
-sub-group, messages are sent using  local broadcast; associated to
-each sub-group is a ``gateway'' in charge of the
-transmission of messages, up and down, between the subgroups. The
-gateways are described as generic pLTSs, playing the role of
-``controllers'' in the pNet node.
-
-\begin{figure}[t]
-\centerline{  \includegraphics[width=0.9\linewidth]{XFIG/SchemaHB2}}
-  \caption{Principle of a Hierarchical Broadcast structure and protocol}
-  \label{fig:hb-scenario}
-\end{figure}
-
-Figure \ref{fig:hb-scenario} shows an instantiation of a HB
-structure, and a possible scenario:
-\begin{itemize}
-\item
-  The HB tree has 3 sub-groups, each with its gateway process, and 6
-  processes scattered in the sub-groups.
-\item
-  The path in green shows the sequence of message exchanges when Process P21 (within
-  group G2) sends a message to process P111 (within group G11).
-\item
-  As the target is not within the local group to which P21 belongs,
-  the initial message $m(111)$ is sent up to group 2, and
-  arrives in gateway $gw2$.
-\item
-  Now the destination belongs to a group that is a sibling of G2, so
-  it is broadcast to all its siblings (sent as $bm(111)$, and
-  received as $m(111)$). It will be simply discarded by
-  gateways or processes that are not involved (here P3), while $gw1$
-  will recognize as being of interest, and in next step send it down
-  to its group.
-\item
-  Sending down is again a broadcast, to all members of sub-group
-  G1. Process P12 will ignore it, while gateway $gw11$ in turn
-  will recognize and forward the message.
-\item
-  Within group G11, process P111 will finally receives message
-  $m(111)$, that terminates our scenario.
-\end{itemize}
-
-Along this paper, we will use this example to illustrate the use of
-pNets as a structured semantic model, with a stress on the fact that
-we represent here HB as a program schema, with unspecified process
-arguments, using open pNets. We will show how the symbolic operational
-semantics of open pNets computes the dynamics of the HB in term of a
-symbolic representation that we call open-transitions, and how we can
-prove equivalences between open systems.
-
-\begin{example} \emph{First step: define the action algebra, with data domains,
-    operators and predicates.}
-  For our HB structure, we use send and receive messages encoded
-  respectively as $m(arg)$ and $im(?var)$ with
-  $arg$ of type \texttt{Address}. HB has a message-based
-  structure, and by convention action names for action reception will
-  be prefix by the letter "i". We abstract away
-  from the payload of the messages, keeping only target addresses in the HB
-  tree as an argument to all messages. Addresses are finite sequences
-  of natural numbers written \texttt{s.i}
-  with \texttt{s} a sequence and i a number. In concrete instantiations, we
-  assume numbers are simple digits, and we write the sequences without
-  the dot, as in ``121''. Then in the model of the
-  gateways, we must be able to decide whether an address is below/above the
-  current address, or in some specific relation, using
-  predicates:\\
-  - \emph{i==j} Syntactic equality between two sequences.\\
-  - \emph{is\_ancestor(i,j)}: $i$ is a (strict) prefix of $j$.\\
-  - \emph{is\_direct\_relative(i,j)}: $i$ and $j$ have a common prefix $k$, $i=k.i1$, $j=k.j1$, with $i1$ of length 1, but $j1$ can be of length equal or greater than 1 ($j$ is a brother or a nephew in the genealogy).\\
-  - \emph{is\_other\_relative(i,j)}: all other cases.\\
-  Note that these 4 predicates are exclusive.
-\end{example}
-
-\begin{example}  \emph{Second step: define the gateway behaviour as a pLTS.}
-
-\begin{figure}[h]
-\centerline{  \includegraphics[width=0.85\linewidth]{ATG/GatewayHB}}
-\caption{Behaviour of a Gateway controller %\TODO{ERIC: change the action syntax}
-  }
-  \label{fig:hb-HBgateway}
-\end{figure}
-Figure \ref{fig:hb-HBgateway} shows the pLTS representing the generic
-gateway controller. From its initial state, it can receive messages
-$ium(?tgt)$ from the subgroup below, or $im(?tgt)$
-coming either from above or from an horizontal broadcast. The details will
-be explained later, together with the model structure and the
-protocol.
-To simplify the notation in the pLTS drawings, we use the following
-conventions: state variables are implicitely subscripted by the
-adequate state number (e.g. $ium(?tgt)$ means $ium(?tgt_2)$), and we
-have ``global'' variables that are defined in all states (here $gid$
-means $gid_0,gid_1,gid_2$).
-
-Note that we use \texttt{if-then-else} or \texttt{case}
-constructs in the pLTS labels. These are mere abbreviations, that can
-be expanded as a set of transitions carrying simple labels with adequate guards.
-\end{example}
-
-\begin{example} \emph{Sorts of pLTSs:}
-  The sort of the gateway in Figure \ref{fig:hb-HBgateway} is:\\
-  $\large\{ um(tgt_s), im(tgt_s), dm(tgt_s), bm(tgt_s), um(tgt_s),
-  ium(tgt_s), DISCARD, \\ERROR(name) \large\}_{s\in\{1,2\}}$
-\end{example}
-
-\begin{figure}[t]
-  \includegraphics[width=1.0\linewidth]{ATG/Inst5}
-  \caption{A Hierarchical Broadcast pNet Structure}\label{fig:hb-pnet-graphical}
- \end{figure}
-
-\begin{example} \emph{pNet structure, and graphical representation}  
-Here we show some parts of the pNet tree expressing our HB
-structure. Figure \ref{fig:hb-pnet-graphical} shows the full pNet
-model in a graphical format, where each box represents a pNet node
-(Groot, G1, ..., G11), a pLTS (gw1, ..., gw11), or a process (P3, ...,
-P111).
-The actions in the sorts of the nodes appear as ports on the boxes,
-and the synchronisation vectors as arrows, or multipoint ``webs''
-drawn as ellipses. For
-example, the webs
-%labelled \texttt{tau}
-in the Groot box
-  correspond to synchronisation vectors expressing a broadcast
-  communication from one of the subnets of Groot (gw1, gw2, or P3), to
-  the others.
-
-  Formally, the root pNet has a structure $<gw1, gw2, G1, G2, P3>$,
-  with G1 and G2 sub-pNets, their associated gateways gw1, gw2
-  pLTSs, and P3 a process Hole. We have 4 possible broadcast communications at the
-  root, corresponding to as many synchronisation vectors; e.g. if gw2 is the sender:
-  $< im(a), bm(a), -, -, im(a)> \to\!\underline{bm(a)}$.
-
-  We define the synchronisation vectors in a parameterised way
-  (independently of a specific HB network configuration) for any
-  pNet node in a HB structure. Let $\widetilde{i}$ be the position of this pNet in the
-  structure.
-   We define here 4 of these synchronisation vectors, that we will
-   use in the next sections to illustrate the semantic rules.
-   %; the full table is listed in Appendix \ref{Appendix:SynchVectors}.
-   In the
-  vectors below,
-  $\widetilde{I_G}=\{gw\widetilde{i}1,..,gw\widetilde{i}p,G\widetilde{i}1,..,G\widetilde{i}p\}$
-   and
-  $\widetilde{I_P}=\{P\widetilde{i}1,..,P\widetilde{i}p\}$ are the sets
-  containing respectively the indexes of sub-nets and holes of the
-  pNet node, $\widetilde{I_{G+P}}$ their union.
-
-  \begin{figure}[h!]
-  \label{fig:HBvectors}
-  \begin{tabular}{|p{1.4cm}|p{11cm}|}
-%% \hline\hline
-%% \multicolumn{3}{|l|}{Hierarchical broadcasting}\\
-  \hline
-  \hline
-$(UG)_{\widetilde{i}k}$\newline
- $k\leq g$&\raisebox{-2pt}{
- $\begin{array}[t]{@{}c@{}c@{}c@{}c@{}c@{}c@{}c@{}c@{}}
- &gw\widetilde{i}1,..&,gw\widetilde{i}k,&..,gw\widetilde{i}g,G\widetilde{i}1,..&,G\widetilde{i}k,&..,G\widetilde{i}g,P\widetilde{i}1,..,P\widetilde{i}p\\
-<\!& -\,-\,-\    &  ,ium(\widetilde{t}),& -\ -\ -\  &,um(\widetilde{t}),&, -\ -\ -\
-&\!>\longrightarrow \underline{um_{\widetilde{i}.k}(\widetilde{t})}
-% $
-%     \symb{sv}_{u(\widetilde{i}k)}\triangleq
-%     <ium_{\widetilde{i}.k}(\widetilde{t})\shortotimes
-%     -^{\widetilde{I_P}}\shortotimes
-%     um_{\widetilde{i}.k}(\widetilde{t})\shortotimes
-%  -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
-%         k\}}}>\longrightarrow
-%     \underline{um(\widetilde{t})}$
-\end{array}$}  \raisebox{-19pt}{~}  \\
-\hline
-     &{\ERIC{Up gateway}: message m is sent
-  up from a group to its gateway, received by the ium action. The
-  resulting action is visible as the (synchronised) $\underline{um}$ }\\
-\hline
- $(UM)_{\widetilde{i}k}$\newline$k\leq g$
- &\raisebox{-2pt}{$\begin{array}[t]{@{}c@{}c@{}c@{}c@{}c@{}c@{}c@{}c@{}}
- &gw\widetilde{i}1,..&,gw\widetilde{i}k,&..,gw\widetilde{i}g,G\widetilde{i}1,..,G\widetilde{i}g,P\widetilde{i}1,..,P\widetilde{i}p\\
- <\!& -\,-\,-\    &  ,um(\widetilde{t}),& -\ -\ -\   -\ -\ -\
- &\!>\longrightarrow \underline{um(\widetilde{t})}
- \end{array}$}\raisebox{-18pt}{~}\\
-\hline
-$(UM)_{\widetilde{i}k}$\newline$k\leq p$
-&\raisebox{-2pt}{$\begin{array}[t]{@{}c@{}c@{}c@{}c@{}c@{}c@{}c@{}c@{}}
-&gw\widetilde{i}1,..,gw\widetilde{i}g,G\widetilde{i}1,..,,G\widetilde{i}g,P\widetilde{i}1,..&,P\widetilde{i}k,&..,P\widetilde{i}p\\
-<\!& -\ -\ -\      -\ -\ -\ &,um(\widetilde{t}),&   -\, -\, -
-&\!>\longrightarrow \underline{um(\widetilde{t})}
-\end{array}$}\raisebox{-18pt}{~}
- % &
-%$\symb{sv}_{!\widetilde{i}}\triangleq
-%    <um_{\widetilde{i}.k}(\widetilde{t})\shortotimes
-%    -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\shortotimes
-%    -^{\widetilde{I_G}}>\longrightarrow
-%    um_{\widetilde{i}.k}(\widetilde{t})$
-\\
-\hline
-     &{\ERIC{Up Message}: message m is sent up from a process
-  or a gateway to the enclosing (= parent) group}\\
-\hline
-
-%% $(BG)_{\widetilde{k}} \ERIC{HB}$ &
-$(HB)_{\widetilde{i}k}$ \newline $k \leq g$
-&\raisebox{-2pt}{$\begin{array}[t]{@{}c@{}c@{}c@{}c@{}c@{}c@{}c@{}c@{}}
-&gw\widetilde{i}1,...&,gw\widetilde{i}k,&..,gw\widetilde{i}g,&G\widetilde{i}1,..,,G\widetilde{i}g&,P\widetilde{i}1,..,
-P\widetilde{i}p \\
-<\!& im(\widetilde{t}), .., im(\widetilde{t}) &, bm(\widetilde{t}),& im(\widetilde{t}),
-..
-im(\widetilde{t}),& -\ -\ -\  &,im(\widetilde{t}),..,im(\widetilde{t})
-&\!>\longrightarrow \underline{bm(\widetilde{t})}
-\end{array}$}\raisebox{-18pt}{~}
-     \\
-\hline
-     &{\ERIC{Horizontal Broadcast}: message m, from a process or a
-  gateway, is broadcast to all its siblings (processes and gateways)
-  inside its group}\\
-\hline\hline\end{tabular}
-\caption{Synchronisation vectors modeling the communication through the HB hierarchy}
-\end{figure}
-
-\end{example}
-
-  \begin{example}\emph{An open-transition.}\label{example:open-trans}
-	After introducing the operational semantics rules, in example
-        \ref{example:deduction-trees}, we shall explain how we 
-	construct this transition using the rules.
-	The transition below corresponds to the application of vector
-        UG at position k=2, and gateway gw2 executing transition
-        $0 \xrightarrow{ium(?tgt2_2)}_{gw2} 2$, storing some address in
-        the state variable $tgt_2$ of gw2..
-
-	\centerline{
-		$\openrule
-		{0 \xrightarrow{a}_{gw2} 2 \\
-			\xrightarrow{b}_{P21}
-			\\ \sm{Pred}_{Root} \\ \emptyset}
-		{\ostate{000} \OTarrow{v} \ostate{020}}
-		$
-	}
-
-	With the predicates
-
-	$\Pred_{Root} = ( a \!=\! ium(?tgt2_2) \land b\!=\!um(t2) \land b\in
-	\Sort_{P21} \land t2 = tgt2_2
-	\land v \!= \! \underline{um(t2)} )  $
-	In the broadcast examples, we do not use assignments and will omit the \Post part of 
-	the open transition.
-\end{example}
-
-\begin{example} \emph{State of a pNet}
-The pNet from Fig. \ref{fig:hb-pnet-graphical} has three leaves (gw1,
-gw2, gw11). So its states will be tuples of length 3,
-e.g. $\triangleleft 102 \triangleright$.
-\end{example}
-
-\begin{example} \emph{Using the operational rules to compute
-    open-transitions}
-  \label{example:deduction-trees}
-
-To build a proof tree, we have to choose one synchronisation vector at
-each instantiation of rule \TrDeux, and one pLTS transition at each
-instantiation of rule \TrUn. Each stage in the proof tree builds one
-open-transition of the corresponding pNet node.  Let us explain in
-detail the first two steps of the
-scenario from Fig. \ref{fig:hb-scenario}:
-
-\begin{figure}[h]
-\centerline{ \includegraphics[width=5cm]{XFIG/HB2} }
-\caption{(open) simplified pNet structure of Hierarchical Broadcast example}
-\label{fig:flattening}
-\end{figure}
-
-\begin{itemize}
-\item Process P21 sends a message towards P111, the combination of sync vectors UM\_21/UG\_2 conveys this message to gateway gw2.
-\item The target address is a relative of gateway gw2, so it
-  broadcasts the message to its siblings using vector HB\_2.
-\end{itemize}
-\end{example}
-
-%% \TODO{but not for local variables of a given pLTS, that MUST keep their
-%%   names through successive use, to keep the dataflow
-%%   information. Still, of course, several instantiations of the same
-%%   pLTS (like gw1, gw2) have distinct local varaibles.}
-
-\paragraph{Building the first transition:}
-
-We use instantiations of the synch vector UM at position 21 (that is a
-hole), and of UG at position 2 (sub-group SG2 in the broadcast hierarchy) gives us :
-\medskip
-
-\noindent
-UM\_21 : $< um(t1), - > \to\!um(t1)$\\
-UG\_2 : $< -, ium(t2), -, -, um(t2) > \longrightarrow \underline{um(t2)}$
-
-\smallskip\noindent
-where the first synch vector (for sub-group SG2) has length 2, and the
-second one (for the root pNet) has length 5. Using once the rule \TrUn,
-and twice rule \TrDeux, we build a proof tree, in which the premisses
-define the behaviour of a gateway pLTS (here
-$0 \xrightarrow{ium(?tgt2_2)}_{gw2} 2$, in which $tgt2_2$ stands for
-the variable $tgt$ of state 2 in gw2), or of a process at a hole
-(e.g. $\xrightarrow{b}_{P21}$ for the process at hole 21).
-The conclusion is an open-transition of the root pNet, with the
-composite state encoding the states of the 3 gateways at the Leaves,
-e.g. $\ostate{000}$.
-
-\begin{mathpar}
-  \inferrule
-      {\inferrule*
-        {0 \xrightarrow{ium(?tgt2_2), \True, \emptyset}_{gw2} 2}
-        {\sm{gw2} \models
-             \openrule {0 \xrightarrow{ium(?tgt2_2)}_{gw2} 2}
-                       {\ostate{0} \xrightarrow{ium(?tgt2_2)} \ostate{2} }
-             }
-        \quad
-        \inferrule* [right={[UM\_21]}]
-           {
-             %\sm{fresh}(b_{P21},v_{SG2})
-           }
-           {\sm{SG2} \models
-             \openrule {\xrightarrow{b}_{P21} \quad \sm{Pred}_{UM\_21}}
-                       {\ostate{-} \xrightarrow{v_{SG2}} \ostate{-} }
-             }
-%           \\ {\sm{fresh}(t1,t2,v) }
-           \quad
-           \sm{Pred}_{UG\_2}
-      }
-      {p\_Root
-     \models
-     \openrule
-         {0 \xrightarrow{ium(?tgt2_2)}_{gw2} 2 \\
-           \xrightarrow{b}_{P21}
-          \\ \sm{Pred1}}
-         {\ostate{000} \OTarrow{v} \ostate{020}}
-      }      ~~ [UG\_2]
-\end{mathpar}
-With:
-
-$Pred_{UM\_21} =  [um(t1)=b \land b\in \Sort_{P21} \land um(t1)=v_{SG2}]$
-
-%% $Pred_{UG\_2} = [ium(?t2) = um(t2) \land v_{SG2} = um(t2) ]$
-
-%% $Pred_{Root} = [ium(?t2) = ium(t2) \land b=um(t1) \land
-%%   b\in \Sort_{P21} \land v_{SG2}=um(t1) \land v_{SG2} = um(t2)
-%%   \land v = \tau]  $
-
-$Pred_{UG\_2} = [ium(t2) = ium(?tgt2_2) \land um(t2) = v_{SG2} \land
-  v = \underline{um(t2)} ]$
-
-$Pred1 = [Pred_{UM\_21} \land Pred_{UG\_2}]  $
-
-That can be simplified (eliminating the vector local variables and the
-intermediate resulting actions), as: $Pred1 = [b\in \Sort_{P21}
-  \land b=um(tgt2_2) \land v=\underline{b} ]  $
-
-%% \TODO{Beware, problem with the ? of ?tgt2: I would prefer having no
-%%   binder (? marker) in the open-automaton predicates, but I do not see
-%% yet how the dataflow will be represented there. OOOOps no more input
-%% var in this transition, t1 is a variable coming from P21.}
-
-\section{Building more transitions of the HB example:}
-\label{appendix:HB-tr2}
-Here we detail the construction of the second transition of our
-scenario:
-
-\begin{mathpar}
-     \openrule
-         {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad
-           2 \xrightarrow{bm(tgt2_2)}_{gw2} 0 \quad
-           \xrightarrow{b}_{P3}
-           \quad Pred_{Root}}
-         {\ostate{020} \OTarrow{v} \ostate{100}}
-\end{mathpar}
-with
-$Pred_{Root} = [tgt1_1=tgt2_2 \land b=um(tgt2_2) \land
-  b\in \Sort_{P3} \land v = \underline{bm(tgt2_2)}]  $
-
-After the first move described in example \ref{example:deduction-trees}, the pLTS of $gw2$ is
-in state 2, ready to emit. We build one
-open-transition for each item in the case statement of its outgoing
-transition; the one we are interested here for our scenario is the
-case where the target address is below $gw1$, corresponding to the
-predicate [$a$=$bm(tgt2_2)$ $\land$ isDirectRelative(2,$tgt2_2$)], and we
-construct the proof tree, reduced here to applications of rule
-\TrUn for transitions of the pLTSs gw1 and gw2, and a single application of rule
-\TrDeux for the synch vector HB at index 2:
-
-\medskip\noindent
-HB\_2 : $< im(t3), bm(t3), im(t3) -, - > \longrightarrow \underline{bm(t3)}$
-
-This illustrates the flow of data through sequences of symbolic moves
-of our example: in the first open-transition, the value (address) sent
-by P21 was stored in the state variable $tgt2_2$. In the second
-transition here, synchronisation within the vector HB\_2 yield the
-predicate $tgt1_1=tgt2_2$, and thus transfers the address to the state
-variable $tgt1_1$ in gw1.
-
-\begin{mathpar}
-  \inferrule
-      {\inferrule
-        {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1}
-        { \sm{gw1} \models
-          \openrule
-              {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad \True}
-              {\ostate{0} \OTarrow{im(?tgt1_1)} \ostate{1}}
-        }
-        \\
-       \inferrule
-           {2 \xrightarrow{bm(tgt2_2)}_{gw2} 0}
-           { \sm{gw2} \models
-             \openrule
-                 {2 \xrightarrow{bm(tgt2_2)}_{gw2} 0 \quad \sm{Pred}_{gw2}}
-                 {\ostate{2} \OTarrow{bm(tgt2_2)} \ostate{0}}
-           }
-           \quad Pred_{HB\_2}
-      }
-           {p\_Root
-     \models
-     \openrule
-         {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad
-           2 \xrightarrow{bm(tgt2_2)}_{gw2} 0 \quad
-           \xrightarrow{b}_{P3}
-           \quad Pred2}
-         {\ostate{020} \OTarrow{v} \ostate{100}}}
-      ~~ [HB\_2]
-\end{mathpar}
-
-$Pred_{gw2} = [\sm{isDirectRelative}(2,tgt2_2)]$
-
-$Pred_{HB\_2} = [im(tgt1_1) = im(t3) \land bm(tgt2_2) = bm(t3) \land b= im(t3) \land b\in 
-\Sort_{P3}  \land v = \underline{bm(t3)}]$
-
-$Pred2 = [Pred_{gw2} \land Pred_{HB\_2} ] $
-
-\medskip
-This can be simplified, eliminating the intermediate variable $t3$ of vector
-HB\_2, while keeping the state variables of $gw_1$ and $gw_2$, the
-intermediate $v$ created by \TrDeux, and the action variable of hole 
-$P3$. This yields finally predicate $Pred2$ :
-
-$Pred2 = [tgt1_1=tgt2_2 \land
-  b\in \Sort_{P3} \land b=um(tgt2_2) \land v = \underline{bm(tgt2_2)}]
-$
-
-\medskip
-Alternatively, we could also have elimated variable $v$, and directly
-show the resulting action $\underline{bm(t3)}]$ in the open
-  transition. This is slightly more compact, and maybe more readable,
-  so we shall use this way in the open-automaton below.
-
-\newpage
-
-Below we show the initial transitions of the automaton of our HB
-system. The full open-automaton has 17 states, and we have not
-computed by hand its full set of transitions. This work would be very
-tedious with pen and paper; we are currently developing a software
-tool to this end.
-
-\begin{figure}[h]
-  \includegraphics[width=0.35\linewidth]{XFIG/HB2}
-\end{figure}
-
-In this open-automaton, we have simplified the predicates and
-eliminated the local variables, excepted those from the occurences of
-the pLTS gw1 and gw2, and from the behaviour of holes.
-
-\begin{figure}[h]
-  \includegraphics[width=\linewidth]{XFIG/HB-OpenAut}
-\end{figure}
-\newpage
-
-\begin{eqnarray*}
-OT_1 & = \openrule
-         {0 \xrightarrow{ium(?tgt2)}_{gw2} 2 \quad
-           \xrightarrow{b1}_{P21}
-          \quad P1}
-         {\ostate{000} \OTarrow{um(tgt2_2)} \ostate{020}}\\
- with & P1 = [b1\in \Sort_{P21} \land b1=um(tgt2_2) ]
- \\
-OT_2 & = \openrule
-         {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad
-           2 \xrightarrow{bm(tgt2_2)}_{gw2} 0 \quad
-           \xrightarrow{b2}_{P3}
-           \quad P2}
-         {\ostate{020} \OTarrow{\underline{bm(tgt2_2)}} \ostate{100}}\\
-         with & P2 = [tgt1_1=tgt2_2 \land IsDirectRelative(2,tgt2_2)
-           \land  b2\in \Sort_{P3} \land b2=um(tgt2_2) ]
-         \\
-OT_3 & = \openrule
-         {1 \xrightarrow{dm(tgt1_1)}_{gw1} 0 \quad
-           0 \xrightarrow{im(?tgt11_1)}_{gw11} 1 \quad
-           \xrightarrow{b3}_{P12}
-           \quad P3}
-         {\ostate{100} \OTarrow{\underline{dm(tgt1_1)}} \ostate{001}}\\
-         with & P3 = [tgt11_1=tgt1_1 \land IsAncestor(1,tgt1_1)
-           \land  b3\in \Sort_{P12} \land b3=im(tgt1_1) ]
-         \\
-OT_4 & = \openrule
-         { 1 \xrightarrow{dm(tgt11_1)}_{gw11} 0 \quad
-           \xrightarrow{b4}_{P111}
-           \quad P4}
-         {\ostate{001} \OTarrow{\underline{dm(tgt11)}} \ostate{000}}\\
- with & P4 = [ b4=im(tgt11_1) \land  b4\in \Sort_{P111} \land IsAncestor(11,tgt11_1) ]
-         \\
-OT_5 & = \openrule
-         {1 \xrightarrow{Discard}_{gw1} 0 \quad
-           \quad P5}
-         {\ostate{100} \OTarrow{\underline{Discard}} \ostate{000}}\\
- with & P5 = [IsDirectRelative(1,tgt1_1) ]
- \\
-OT_6 & = \openrule
-         { 2 \xrightarrow{Discard}_{gw2} 0 \quad
-           \quad P6}
-         {\ostate{020} \OTarrow{\underline{Discard}} \ostate{000}}\\
- with & P6 = [ IsAncestor(2,tgt2_2) ]
- \\
-OT_7 & = \openrule
-         {0 \xrightarrow{im(?tgt1_1)}_{gw1} 1 \quad
-          0 \xrightarrow{im(?tgt2_1)}_{gw2} 1 \quad
-          \xrightarrow{b7}_{P3}\quad
-           \quad P7}
-         {\ostate{000} \OTarrow{im(?a)} \ostate{110}}\\
- with & P7 = [ tgt1_1 = tgt2_1 = a \land b7\in \Sort_{P3} \land b7 = im(?a)  ]
- \\
-OT_8 & = \openrule
-         {2 \xrightarrow{Discard}_{gw2} 0 \quad
-           \quad P8}
-         {\ostate{110} \OTarrow{Discard} \ostate{100}}\\
- with & P8 = [ IsDirectRelative(2,tgt2_1) ]
-\end{eqnarray*}
-
-\end{document}
-
-\section{ABP}
-I have collected here all previous items about ABP, in case we wnat to
-reuse them later
-
-\begin{figure}[t]
-  \centerline{
-   \includegraphics[width=8cm]{XFIG/ABP-Schema}
-   }
-   \caption{Schema of the ABP example}  \label{ABP:Schema}
-\end{figure}
-
-\section{Discussion on substitution, matching, unification}
-
-\TODO{this is far from being final... What should we leave here
-  ? a generic definition of what must be part of the Action Algebra
-  definition, substitution, protected variables; and
-  move to other sections the application and examples of these.
-In fact we currently do not use any notion of substitution, nor
-protect variables. Only these predicates, built as sets of equations,
-with a lot of fresh variables...}
-
-\ERIC{[this text in blue is NOT supposed to stay here as such. Just
-    guidelines towards identifying what we need to set up]
-  To define the operational semantics of pNets, we need only two core
-operations on action expressions: specialisation and unification.
-\begin{itemize}
-\item when composing pNets, substituting a pNet for a hole, each action in
-the subnet sort has to match one action of the hole sort, but may be
-more specific (substitution).
-\item when building a proof tree from a synch vector, we collect a
-  number of substitutions from the involved processes, and we have to
-  match them with the action expressions in the vector. The result is
-  a substitution for the variables of the global action, together with
-  a predicate, built from the guards of the controllers and predicates
-  of the subnets.
-\end{itemize}
-In some cases, substitutions are results of full unification between
-action expressions, but in other cases it may be disymetric in the
-sense that some variables can be substituted, and other not. We can
-formalise this in term of ``protected variables'' in the unification,
-opposed to ``input variables'' that can be arbitrarily substituted (=
-can accept any value, like in classical value-passing algebra communication).}
-
-\section{Future papers...}
-
-I removed from here all appendices that were not directly related to this paper.
-They will be providing subjects for future research (internships ?) and future papers, including:
-
-\begin{itemize}
-  \item Is open (strong) bisim compatible with pNet composition operator (as defined in PdP paper) ?
-  \item Is Open-bisimulation compatible with closed bisimulation ?
-    \item Effective algorithm for 1) checking strong bisimulation (given a state partition) 2) computing the coarsest partition (if it exists).
-\item Model-checking Open-Automata:
-This may come to be simpler to define and implement than FH-bisimulation.
-\item FH-Refinement (and maybe even weak bisimulation if we do not find the time and/or space to have it here)
-\item Fulll use-case on Hierarchical Broadcast
-\end{itemize}
-
-\section{Full definition of the HB pNet model}
-\label{Appendix:SynchVectors}
-
-  The table in Fig. \ref{fig:HBvectors} lists the synchronisation
-  vectors used in all 3 algorithms and their variants. The vector
-  naming schema is the following: the first letter encodes the direction
-  of the message: U(p), D(own), H(orizontal); the second letter its
-  type: B(roadcast) G(gateway-group) or M(simple message).
-
-  Additionally, there are 2 special vectors, DIS for (silent) Discard
-  events, and ERR for (visible) Error events.
-
-  Among the 6 basic vectors, 3 of them (UG, DG, UM) are shared by all
-  algorithms, DB is used by Full and hierarchical braodcast, while the
-  last 2, HM and HB are specific to horizontal messages of Unicats and
-  hierarchical brodcast respectively.
-
-  \TODO{missing the variants here...}
-
-\begin{figure}[h!]
-  \label{fig:HBvectors}
-\begin{tabular}{|p{1.6cm}|p{8.8cm}|l|}
-%% \hline\hline
-%% \multicolumn{3}{|l|}{Hierarchical broadcasting}\\
-  \hline
-  \hline
-\multicolumn{3}{|p{12cm}|}{\ERIC{Need a short explanation about notations here: indices, indexed actions to be instanciated to match the terms in the sorts, ...? }}\\
-  \hline
- %% $(UC)_{\widetilde{k}} \ERIC{UG}$ & $
- $(UG)_{\widetilde{k}}$ & $
-     \symb{sv}_{u(\widetilde{i}.k)}\triangleq
-     <?um_{\widetilde{i}.k}(\widetilde{t})\shortotimes
-     -^{\widetilde{I_P}}\shortotimes
-     !m_{\widetilde{i}.k}(\widetilde{t})\shortotimes
-     -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
-         k\}}}>\longrightarrow \tau(
-     m_{\widetilde{i}.k}(\widetilde{t}))$ &
-     $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}$\\
-\hline
-     &\multicolumn{2}{|p{10cm}|}{\ERIC{Up gateway}: message m is sent up from a group to its gateway}\\
-\hline
-%% $(DG)_{\widetilde{k}} \ERIC{DB}$&
-$(DB)_{\widetilde{k}}$&
-$\symb{sv}_{?\widetilde{i}}\triangleq
-     <?m_{\widetilde{i}.k}(\widetilde{t})\shortotimes
-     -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\shortotimes
-     -^{\widetilde{I_G}}>\longrightarrow
-     ?dm_{\widetilde{i}}(\widetilde{t})$&$\widetilde{k}=\widetilde{i}.k\in \widetilde{I_{G+P}}$\\
-     \hline
-     &\multicolumn{2}{|p{10cm}|}{\ERIC{Down Broadcast}: a message m received by a group is
-       forwarded (broadcast) to all elements of the group, meaning to
-       all processes and gateways inside.}\\
-\hline
-$(UM)_{\widetilde{k}}$&
-$\symb{sv}_{!\widetilde{i}}\triangleq
-    <!um_{\widetilde{i}.k}(\widetilde{t})\shortotimes
-    -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\shortotimes
-    -^{\widetilde{I_G}}>\longrightarrow
-    !um_{\widetilde{i}.k}(\widetilde{t})$ & $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_{G+P}}$\\
-\hline
-     &\multicolumn{2}{|p{10cm}|}{\ERIC{Up Message}: message m is sent up from a process
-  or a gateway to the enclosing (= parent) group}\\
-\hline
-
-%% $(BG)_{\widetilde{k}} \ERIC{HB}$ &
-$(HB)_{\widetilde{k}}$ &
-$\symb{sv}_{b(\widetilde{i}.k)}\triangleq
-    <?m_{\widetilde{i}.j}^{\forall j\in I_K}(\widetilde{t})
-    \shortotimes !bm_{\widetilde{i}.k}(\widetilde{t})
-    \shortotimes -^{\widetilde{I_G}}>\longrightarrow \tau( bm(\widetilde{t}))$ &
-    $I_K = \{k/\widetilde{i}.k\in \widetilde{I_{G+P}}\}$, \\ &  &  and
-    $\widetilde{k}=\widetilde{i}.k$ \\
-\hline
-     &\multicolumn{2}{|p{10cm}|}{\ERIC{Horizontal Broadcast}: message m, from a process or a
-  gateway, is broadcast to all its siblings (processes and gateways)
-  inside its group}\\
-
-\hline
-%% $(DC)_{\widetilde{k}} \ERIC{DG}$ &
-$(DG)_{\widetilde{k}}$ &
-$\symb{sv}_{?\widetilde{i}}\triangleq
-     <!dm_{\widetilde{i}.k}(\widetilde{t})\shortotimes
-     -^{\widetilde{I_P}}\shortotimes
-     ?dm_{\widetilde{i}.k}(\widetilde{t})\shortotimes
-     -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}}
-     >\longrightarrow
-     \tau(m_{\widetilde{i}.k}(\widetilde{t}))$,
-%      <?m_{\widetilde{i}.k}^{\forall k\in
-%        I_K}(\widetilde{t})\shortotimes
-%      -^{\widetilde{I_P}}\shortotimes -^{\widetilde{I_G}}>\longrightarrow
-     %      ?m_{\widetilde{i}}(\widetilde{t})$
-     & $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}$\\
-
-\hline
-     &\multicolumn{2}{|p{10cm}|}{\ERIC{Down Gateway}: message $m$ is sent down from a gateway
-to the corresponding subgroup; it should then be forwarded inside the
-subgroup, e.g. with $(DM)_{\widetilde{k}}$}\\
-\hline
-%% $(DK)_{\widetilde{k}} \ERIC{DM}$&
-$(DM)_{\widetilde{k}}$&
-$\symb{sv}_{!\widetilde{i}}\triangleq
-    <  ?m_{\widetilde{i}.k}(\widetilde{t})\shortotimes
-    -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\shortotimes
-    -^{\widetilde{I_G}}>\longrightarrow ?m_{\widetilde{i}}(\widetilde{t})$
-    & $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_{G+P}}$\\
-\hline
-     &\multicolumn{2}{|p{10cm}|}{\ERIC{Down Message}: Unicast version of (DB): m received
-  by a group is forwarded to one specific element $i.k$ of the group}\\
-\hline
-
-$(HM)_{\widetilde{k}}$&
-$\symb{sv}_{!\widetilde{i}}\triangleq
-   $\\
-\hline
-&\multicolumn{2}{|p{10cm}|}{\ERIC{Horizontal Message}: optimized
-  version of Unicast: message m, from a process or a
-  gateway, is broadcast to one of its its siblings
-  inside the same group}\\
-
-\hline\hline
-$(DIS)_{\widetilde{k}}$&
-     $\symb{sv}_{u(\widetilde{i}.k)}\triangleq
-     <Discard\shortotimes
-     -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\shortotimes
-     -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
-         k\}}}>\longrightarrow \tau(DIS)$ &
-     $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}$\\
-\hline
-     &\multicolumn{2}{|p{10cm}|}{\ERIC{DISCARD events} occur in gateways
-  under HB protocol, after receiving a broadcast message which
-  target address is a sibling of the gateway; this message is
-  DISCARDED silently }\\
-\hline
-$(ERR)_{\widetilde{k}}$&
-     $\symb{sv}_{u(\widetilde{i}.k)}\triangleq
-     <Error\shortotimes
-     -^{\widetilde{I_{G+P}}\backslash\{\widetilde{i}\cdot k\}}\shortotimes
-     -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
-         k\}}}>\longrightarrow Error(\widetilde{k})$ &
-     $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}$\\
-\hline
-     &\multicolumn{2}{|p{10cm}|}{\ERIC{ERROR events} may occur in gateways
-  in 2 cases: either if the message is targeted to a gateway address,
-  that is an error from the emittor (ERR "BadTarget"); or if a gateway
-  receives from its parent or brother a message that should not go
-  within its subgroup, that is a protocol error (ERR "WrongWay").
-  In both cases the ERR message will be transmitted up, for the sake
-  of verification }\\
-\hline\hline\end{tabular}
-\caption{Synchronisation vectors modeling the communication through the HB hierarchy}
-\end{figure}
-
-\section{The  Open Transitions of Broadcasting}
-% \TODO{Min: to modify the tables. }
-
-%%mofication of Table 1
-
-\begin{figure}[h]
-\centerline{ \includegraphics[width=5cm]{XFIG/HB2} }
-\caption{(open) pNet structure of Hierarchical Broadcast example}
-\label{Fig:simpleHBStruct}
-\end{figure}
-
-Figure \ref{Fig:simpleHBStruct} recalls the structure of the pNet tree
-for HB example structure, in which gw1, gw2, gw11 are leaves, and P3,
-P12, P21, P22, P111 are holes.
-
-The following tables list the open-transition derivable from two of
-the first states of the open-automaton of this pNet, including the 2 first
-transitions of our scenario, as explained in section \ref{}.
-
-\noindent
-\begin{tabular}{|p{2.8cm}|p{9cm}|l|}
-\hline\hline
-\multicolumn{3}{|l|}{from state $\ostate{000}$}\\
-\hline
-HB(3) &
-\{gw1, gw2\} \{P3\}  \{$a_{gw1}$=$a_{gw2}$=?m(t), $b_{P3}$=!bm(t'), v=$\tau$,[t=t']\} &
-$\ostate{110}$\\
-\hline
-HB(12)&
-\{gw11\} \{P12\} \{$a_{gw11}$=?m(t), $b_{P12}$=!bm(t'), v=$\tau$, [t=t' ]\} & $\ostate{001}$\\
-\hline
-DB&
-\{gw1, gw2\}\{\}\{$a_{gw1}$=$a_{gw2}$=?m(t), v=?dm(t'),  [t=t']\}&$\ostate{110}$\\
-\hline
-UG(1)(UM(12)) &
-\{gw1\},  \{P12\} \{$a-{gw1}$=?um(t), $b_{P12}$=!um(t'), v=$\tau$, [t=t']\} &
-$\ostate{200}$\\
-\hline
-UG(2)(UM(k)) ${}^{k \in \{21,22\}}$ &
-\{gw2\},  \{Pk\} \{$a_{gw2}$=?um(t), $b_{Pk}$=!um(t'),v=$\tau$, [t=t']\} &
-$\ostate{020}$\\
-\hline
-UG(11)(UM(111)) &
-\{gw11\},  \{P111\} \{$a_{gw11}$=?um(t), $b_{P111}$=!m(t),v=$\tau$, [t=t']\} &
-$\ostate{002}$\\
-\hline\hline
-\end{tabular}
-\vskip 0.3cm
-
-\NOTE{ERIC: one transition of the <020> table, from the draft on my white board}
-
-\noindent
-\begin{tabular}{|p{2.8cm}|p{9cm}|l|}
-\hline\hline
-\multicolumn{3}{|l|}{from state <020>}\\
-\hline
-HB(2)&
-\{gw1,gw2\} \{P3\} \{a1=?m(t), a2=!bm(t'), a3=?m(t'), v=tau, [t=t'=t'' $\land$ isDirRel(t,2)]\} & <100>\\
-\hline
-HB(12)&
-\{gw11\} \{P12\} \{a11=?m(t), a12=!bm(t'),  v=tau, [t=t']\} & <021>\\
-\hline
-UG(1)(UM(12)) &
-\{gw1\},  \{P12\} \{a1=?um(t), a12=!um(t'), v=tau,  [t=t'] \} &
-<220>\\
-\hline
-UG(11)(UM(111)) &
-\{gw11\},  \{P111\} \{a11=?um(t), P111=!m(t),v=tau, [t=t']\} &
-<022>\\
-\hline
-ERR(2)&
-\{g2\} \{\} \{a2=Error, v=Error2,[t=2]\}&<000>\\
-\hline
-DiS(2)&
-\{g2\} \{\} \{a2=DIS, v=DIS2,[Ancestor(2, t)]\} &
-<000>\\
-\hline
-\hline
-\end{tabular}
-\vskip 0.3cm
-
-%
-%\noindent
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <1, 1, 0>}\\
-%\hline
-%HB(12)&
-%\{g11\} \{P12\} \{a11=?m(a), a12=!bm(a), v=tau\} & <1, 1, 1>\\
-%\hline
-%UM(k) ${}^{k \in \{3,12\}}$&
-%\{\}\{Pk\}\{ak=!um(a),v=!um(a), isOtherRelative(3, a)\}&<1, 1, 0>\\
-%\hline
-%UM(1)&
-%\{g1\}\{\}\{a1=!um(a),v=!um(a), isOtherRelative(1, a)\}&<0, 1, 0>\\ \hline
-%UM(2)&
-%\{g2\}\{\}\{a2=!um(a),v=!um(a), isOtherRelative(2, a)\}&<1, 0, 0>\\ \hline
-%DG(1)&
-%\{g1\}\{SG1\}\{a1=!dm(a),sg1=?dm(a),v=tau\}&<0, 1, 0>\\ \hline
-%DG(2)&
-%\{g2\}\{SG2\}\{a2=!dm(a),sg2=?dm(a), v=tau\}&<1, 0, 0>\\ \hline
-%
-%DIS(1)&
-%\{g1\} \{\} \{a1=Discard, v=tau\} &
-%<0, 1, 0>\\
-%\hline
-%DIS(2)&
-%\{g2\} \{\} \{a2=Discard, v=tau\} &
-%<1, 0, 0>\\
-%\hline
-%ERR(1)&
-%\{g1\} \{\} \{a1=Error, v=Error1\}, &
-%<0, 1, 0>\\
-%\hline
-%ERR(2)&
-%\{g2\} \{\} \{a2=Error, v=Error2\} &
-%<1, 0, 0>\\
-%\hline
-%UG(11) &
-%\{g11\},  \{SG11\} \{a11=?um(a), sg11=!m(a),v=tau, isOtherRelative(11, a)\} &
-%<1, 1, 2>\\
-%\hline\hline
-%\end{tabular}
-%\vskip 0.3cm
-%\noindent
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <0, 0, 1>}\\
-%\hline
-%HB(3) &
-%\{g1, g2\} \{P3\} \hfill \{a1=a2=?m(a), a3=!bm(a), v=tau\} &
-%<1, 1, 1>\\
-%\hline
-%DB &
-%\{g1, g2\} \{\} \{a1=a2=?m(a), v=?dm(a)\} &
-%<1, 1, 1>\\
-%\hline
-%UG(1) &
-%\{g1\},  \{SG1\} \{a1=?um(a), sg1=!m(a),v=tau, isOtherRelative(1, a)\} &
-%<2, 0, 1>\\
-%\hline
-%UG(2) &
-%\{g2\},  \{SG2\} \{a2=?um(a), sg2=!m(a),v=tau, isOtherRelative(2, a)\} &
-%<0, 2, 1>\\
-%\hline
-%DG(11)  &
-%% $\emptyset$
-%\{g11\} \{SG11\} \{a11=!dm(a),sg11=?dm(a) v=tau,\} & <0, 0, 0>\\
-%\hline
-%
-%DIS11 &
-%\{g11\},\{\}\{a11=Discard, v=tau \}&<0, 0, 0>\\
-% \hline
-% ERR11 &
-%\{g11\},\{\}\{a11=Error, v=Error11 \}&<0, 0, 0>\\
-% \hline\hline
-%\end{tabular}
-%
-%\vskip 0.3cm
-%There is the case of Unicast.
-%\vskip 0.3cm
-%\noindent
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <0, 0, 0>}\\
-%\hline
-%DM1 &
-%\{g1\} \{P3\}  \{a1=?m(a), a3=!m(a), v=tau, isDirectRelative(1,a)\} &
-%<1, 0, 0>\\
-%\hline
-%DM2 &
-%\{g2\} \{P3\}  \{a1=?m(a), a3=!m(a), v=tau, isDirectRelative(2,a)\} &
-%<0, 1, 0>\\
-%\hline
-%DM11 &
-%\{g11\} \{P13\}  \{a11=?m(a), a13=!m(a), v=tau, isDirectRelative(11,a)\} &
-%<0, 0, 1>\\
-%\hline\hline
-%\end{tabular}
-%\vskip 0.3cm
-%\noindent
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <1, 0, 0>}\\
-%\hline
-%DG1 &
-%\{g1\} \{SG1\}  \{a1=!dm(a), sg1=?dm(a), v=tau, isDirectRelative(1,a)\} &
-%<0, 0, 0>\\
-%\hline
-%UM1 &
-%\{g1\} \{\}  \{a1=!um(a), v=!um(a)\} &
-%<0, 0, 0>\\
-%\hline
-%DM2 &
-%\{g2\} \{P3\}  \{a1=?m(a), a3=!m(a), v=tau, isDirectRelative(2,a)\} &
-%<1, 1, 0>\\
-%\hline
-%DM11 &
-%\{g11\} \{P13\}  \{a11=?m(a), a13=!m(a), v=tau, isDirectRelative(11,a)\} &
-%<1, 0, 1>\\
-%\hline
-%ERR(1)&
-%\{g1\} \{\} \{a1=Error, v=tau\} &
-%<0, 0, 0>\\
-%\hline\hline
-%\end{tabular}
-%
-%\vskip 0.3cm
-%
-%\noindent
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <1, 1, 0>}\\
-%\hline
-%DG1 &
-%\{g1\} \{SG1\}  \{a1=!dm(a), sg1=?dm(a), v=tau, isDirectRelative(1,a)\} &
-%<0, 1, 0>\\
-%\hline
-%DG2 &
-%\{g2\} \{SG2\}  \{a2=!dm(a), sg2=?dm(a), v=tau, isDirectRelative(2,a)\} &
-%<1, 0, 0>\\
-%\hline
-%UM1 &
-%\{g1\} \{\}  \{a1=!um(a), v=!um(a)\} &
-%<0, 1, 0>\\
-%\hline
-%UM2 &
-%\{g2\} \{\}  \{a2=!um(a), v=!um(a)\} &
-%<1, 0, 0>\\
-%\hline
-%DM11 &
-%\{g11\} \{P13\}  \{a11=?m(a), a13=!m(a), v=tau, isDirectRelative(11,a)\} &
-%<1, 1, 1>\\
-%\hline
-%ERR(1)&
-%\{g1\} \{\} \{a1=Error, v=tau\} &
-%<0, 1, 0>\\
-%\hline
-%ERR(2)&
-%\{g2\} \{\} \{a2=Error, v=tau\} &
-%<1, 0, 0>\\
-%\hline\hline
-%\end{tabular}
-
-\section{Encapsulating Process arguments}
-In Section \ref{section:processSort} we described the Sort of
-processes in the holes of the herarchical broadcast architecture.
-Here we present a more general solution, using a small pNet as a
-filter encapsulating each of the holes. The filter is in
- charge of relabeling the messages
-from the process depending on their destination, and filtering the
-incoming messages, discarding those received by broadcast, but target
-to other processes. This pNet is shown in the following figure:
-
-\centerline{  \includegraphics[width=0.8\linewidth]{ATG/ProcessFilter}}
-
-This solution has the benefit of allowing any process as an argument
-fitting the hole, without specific constraints on its sort. The price
-is that the pNet structure is a bit more complex, so the open
-transitions and open automata will be bigger also. Moreover the filter
-has states, and this introduces some additional states and
-tau-transitions in the open-automaton.
-
-\section{{pNets Model for Broadcast Flat groups  (BF-pNets):
-    definition}\label{sec:bf-pnets-def}}
-Given a $HB-\pNet$, we can flatten it to decrease the number of layers
-of hierarchical structures using a {\em Flattening Operator}
-$\bowtie$.
-This operation replaces one or several subgroups in the hierarchical
-structure by their content. The corresponding old controllers
-(gateways) won't exist after flattening. Fig. \ref{fig:flattening}
-shows the flattening operator at work, on 2 subgroups SG1 and SG2, at the
-toplevel of the example.
-\begin{definition}[Flattening Operation]
-Assume a $HB-\pNet$ has the structure:
-$\mylangle gw_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}},  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, sg_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}}\myrangle$
-where
-$ \forall \widetilde{g}\in \widetilde{I_G}$,  the $sg_{\widetilde{g}}$ has the $HB-\pNet$ structure:
- $\mylangle gw_{\widetilde{g}\cdot g_i}^{g_i\in I_{G_{\widetilde{g}}}},  pc_{\widetilde{g}\cdot p_j}^{p_j\in I_{P_{\widetilde{g}}}}, sg_{\widetilde{g}\cdot g_i}^{g_i\in I_{G_{\widetilde{g}}}}\myrangle $.
- \medskip
-
- Then
-the flattening map
-$\bowtie_{\widetilde{g}}: HB-pNets\longrightarrow HB-pNets$, where\\
-
- \medskip
- $\bowtie_{\widetilde{g}}(HB-\pNet)\triangleq \mylangle gw_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g}\}}, gw_{\widetilde{g}\cdot g_i}^{g_i\in I_{G_{\widetilde{g}}}},  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, pc_{\widetilde{g}.\cdot p_j}^{p_j\in I_{P_{\widetilde{g}}}},sg_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g}\}}, sg_{\widetilde{g}\cdot g_i}^{g_i\in I_{G_{\widetilde{g}}}}\myrangle$.
- \medskip
-
-The flattening operator shows one subgroup $sg_{\widetilde{g}}$ can be flatten to one hole of his father group which is linked the gateway $gw_{\widetilde{g}}$, the gateways,the processes ,and the holes of $sg_{\widetilde{g}}$ become the gateways, the processes, and the holes of his father group instead of itself and the gateway that it is linked.
-
-Actually, for any subgroup (hole) of the group, the flattening operation can be done in parallel without the order.
-We denote that  $\bowtie_{\widetilde{I_G}}\triangleq\Sigma_{\widetilde{g}\in{\widetilde{I_G}}}\bowtie_{\widetilde{g}}$, where:
-
- $\bowtie_{\widetilde{I_G}}(HB-\pNet)\triangleq \mylangle  gw_{\widetilde{g}\cdot g_i}^{\widetilde{g}\in \widetilde{I_G}, g_i\in I_{G_{\widetilde{g}}}},  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, pc_{\widetilde{g}\cdot p_j}^{\widetilde{g}\in \widetilde{I_G}, p_j\in I_{P_{\widetilde{g}}}}, sg_{\widetilde{g}\cdot g_i}^{\widetilde{g}\in \widetilde{I_G}, g_i\in I_{G_{\widetilde{g}}}}\myrangle$.
-\end{definition}
-
-Especially, if some $\widetilde{g_0}\in{\widetilde{I_G}}$, the $sg_{\widetilde{g_0}}$ has the $HB-\pNet_{\widetilde{g_0}}$ structure: $\mylangle -,  pc_{\widetilde{g_0}\cdot p_j}^{p_j\in I_{P_{\widetilde{g}}}}, -\myrangle$.
-
- $\bowtie_{\widetilde{g_0}}(HB-\pNet)\triangleq \mylangle gw_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g}\}},   pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, pc_{\widetilde{g_0}\cdot p_j}^{ p_j\in I_{P_{\widetilde{g}}}},sg_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g}\}}\myrangle$.
-
-% If all the subgroups $sg_{\widetilde{g}}$ have the similar structures to $sg_{\widetilde{g_0}}$, $\forall \widetilde{g}\in \widetilde{I_G}$, we have
-%
-%  $\bowtie_{\widetilde{I_G}}(HB-\pNet)\triangleq \mylangle -,  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, pc_{\widetilde{g}\cdot p_j}^{\widetilde{g}\in \widetilde{I_G}, p_j\in I_{P_{\widetilde{g}}}}, -\myrangle$.
-
-\medskip
-%
-%\begin{definition}[Equivenlence]
-%\NOTE{The equivalence between $HB-\pNet$ and $BF-\pNet$ should be defined.}
-%\end{definition}
-
- Let $HB-\pNet$ node have the structure $\mylangle gw_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}},  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, sg_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}}\myrangle$, with some subgroup the $sg_{\widetilde{g_0}}$ who has the  structure:
- $\mylangle gw_{\widetilde{g_0}\cdot g_i}^{g_i\in I_{G_{\widetilde{g_0}}}},  pc_{\widetilde{g_0}\cdot p_j}^{p_j\in I_{P_{\widetilde{g_0}}}}, sg_{\widetilde{g_0}\cdot g_i}^{g_i\in I_{G_{\widetilde{g_0}}}}\myrangle $, has one corresponding flatten broadcast open $\pNet$ by the flattening operator $\bowtie_{\widetilde{g_0}}$, i.e.
-$\mylangle gw_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g_0}\}}, gw_{\widetilde{g_0}\cdot g_i}^{g_i\in I_{G_{\widetilde{g}}}},  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, pc_{\widetilde{g_0}.\cdot p_j}^{p_j\in I_{P_{\widetilde{g}}}},sg_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g_0}\}}, sg_{\widetilde{g_0}\cdot g_i}^{g_i\in I_{G_{\widetilde{g}}}}\myrangle$.
-
-\section{Sketch of the proof}
-\label{sec:proof-sketch}
-
-In this section we will describe a proof of equivalence between a HB
-pNet node (seen as an open pNet), with the corresponding flatten
-broadcast open pNet. From this equivalence, it is easy to derive the
-equivalence of a fully instantiated (= closed) HB-pNet structure with
-the corresponding flatten pNet.
-
-\begin{theorem}
-Any $\mathcal{HB-\pNet}$ node is FH-bisimular to the corresponding $\mathcal{BF-\pNet}$ node by the flatting operator $\bowtie$, that is, \\
-$\mylangle gw_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}},  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, sg_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g_0}\}},\mylangle gw_{\widetilde{g_0}\cdot g_i}^{g_i\in I_{G_{\widetilde{g_0}}}},  pc_{\widetilde{g_0}\cdot p_j}^{p_j\in I_{P_{\widetilde{g_0}}}}, sg_{\widetilde{g_0}\cdot g_i}^{g_i\in I_{G_{\widetilde{g_0}}}}\myrangle  \myrangle \approx_{FH} \\ \mylangle gw_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g_0}\}}, gw_{\widetilde{g_0}\cdot g_i}^{g_i\in I_{G_{\widetilde{g}}}},  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, pc_{\widetilde{g_0}.\cdot p_j}^{p_j\in I_{P_{\widetilde{g}}}},sg_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}\setminus\{\widetilde{g_0}\}}, sg_{\widetilde{g_0}\cdot g_i}^{g_i\in I_{G_{\widetilde{g}}}}\myrangle$.
-\end{theorem}
-
-The sketch we give here considers one particular pNet node, with 2
-subgroups, and a specific number of processes in each root- and sub-
-groups. Also we make some hypotheses on the sorts of the processes.
-Clearly the full proof will have to deal with generalisations of this
-particular case.
-
-\begin{figure}[h]
-\includegraphics[width=6cm]{XFIG/HB2}
-\hspace{1cm}
-\includegraphics[width=5cm]{XFIG/B2}
-\caption{(open) pNet structure of Hierarchical and flat example}
-\label{fig:flattening}
-\end{figure}
-
-\paragraph{More precisely:}
-
-\paragraph{Principles of the proof:}
-
-We start from the hierarchical pNet, build all its possible behaviours
-(building proof trees from possible synch vectors of the pNet, and
-possible actions in the sorts of holes), then show that there is a
-corresponding behaviour for the flat pNet. Similar method is then
-applied in the symetrical direction.
-
-A state of the hierarchical pNet will be a hierarchical vector of
-``states'', in which we shall represent the state of a controller with
-its name followed by the state index (gateways have only two states,
-numered \{0,1\}); and state of holes with simply the name of the hole.
-To keep state structure compact and keep readability, we show pLTS
-states by their number, subscripted by the name of the gateway. For
-processes and sub-groups, that have no states, we only show their name.
-%
-%
-%
-%\noindent
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <0, 0, 0>}\\
-%\hline
-%Bm(3) &
-%\{g1, g2\} \{P3\} \hfill \{a1=a2=?bm(a), a3=!m(a), v=tau\} &
-%<1, 1, 0>\\
-%\hline
-%Bm(12)&
-%\{g11\} \{P12,P13\} \{a11=a13=?um(a), a12=!m(a), v=tau\} & <0, 0, 1>\\
-%\hline
-%Bm(13)&
-%\{g11\} \{P12,P13\} \{a11=a12=?um(a), a13=!m(a), v=tau\} & <0, 0, 1>\\
-%\hline
-%DA &
-%\{g1, g2\} \{P3\} \{a1=a2=a3=?bm(a), v=?m(a)\} &
-%<1, 1, 0>\\
-%\hline
-%Um(1) &
-%\{g1\},  \{SG1\} \{a1=?bm(a), sg1=!m(a),v=tau, isOtherRelative(1, a)\} &
-%<2, 0, 0>\\
-%\hline
-%Um(2) &
-%\{g2\},  \{SG2\} \{a2=?bm(a), sg2=!m(a),v=tau, isOtherRelative(2, a)\} &
-%<0, 2, 0>\\
-%\hline
-%Um(11) &
-%\{g11\},  \{SG11\} \{a11=?bm(a), sg11=!m(a),v=tau, isOtherRelative(11, a)\} &
-%<0, 0, 2>\\
-%\hline
-%UA(k) ${}^{k \in \{3,12,13,21\}}$ &
-%% $\emptyset$
-%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <0, 0, 0>\\
-%\hline\hline
-%\end{tabular}
-%
-%\noindent
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <1, 1, 0>}\\
-%\hline
-%Bm(12)&
-%\{g11\} \{P12,P13\} \{a11=a13=?um(a), a12=!m(a), v=tau\} & <1, 1, 1>\\
-%\hline
-%Bm(13)&
-%\{g11\} \{P12,P13\} \{a11=a12=?um(a), a13=!m(a), v=tau\} & <1, 1, 1>\\
-%\hline
-%UA(3)&
-%\{\}\{P3\}\{a3=!um(a),v=!m(a), isOtherRelative(3, a)\}&<1, 1, 0>\\
-%\hline
-%UA(1)&
-%\{g1\}\{\}\{a1=!um(a),v=!m(a), isOtherRelative(1, a)\}&<0, 1, 0>\\ \hline
-%UA(2)&
-%\{g2\}\{\}\{a2=!um(a),v=!m(a), isOtherRelative(2, a)\}&<1, 0, 0>\\ \hline
-%$Dm_1(DA_1)$ &
-%\{g1,g11\}\{SG1,P12,P13\}\{a1=!dm(a), sg1=?m(a),a11=a12=a13=?bm(a), v=tau, isDirectRelative(1,a)\}&<0, 1, 1>\\ \hline
-%$Dm_2(DA_2)$ &
-%\{g2\}\{SG2,P21\}\{a2=!dm(a), sg2=?m(a), a21=?bm(a), v=tau, isDirectRelative(2,a)\}&<1, 0, 0>\\ \hline
-%DISCARD(1)&
-%\{g1\} \{\} \{a11DISCARD, v=tau\} &
-%<0, 1, 0>\\
-%\hline
-%DISCARD(2)&
-%\{g2\} \{\} \{a2=DISCARD, v=tau\} &
-%<1, 0, 0>\\
-%\hline
-%Um(11) &
-%\{g11\},  \{SG11\} \{a11=?bm(a), sg11=!m(a),v=tau, isOtherRelative(11, a)\} &
-%<1, 1, 2>\\
-%\hline\hline
-%\end{tabular}
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <0, 0, 1>}\\
-%\hline
-%Bm(3) &
-%\{g1, g2\} \{P3\} \hfill \{a1=a2=?bm(a), a3=!m(a), v=tau\} &
-%<1, 1, 1>\\
-%\hline
-%DA &
-%\{g1, g2\} \{P3\} \{a1=a2=a3=?bm(a), v=?m(a)\} &
-%<1, 1, 1>\\
-%\hline
-%Um(1) &
-%\{g1\},  \{SG1\} \{a1=?bm(a), sg1=!m(a),v=tau, isOtherRelative(1, a)\} &
-%<2, 0, 1>\\
-%\hline
-%Um(2) &
-%\{g2\},  \{SG2\} \{a2=?bm(a), sg2=!m(a),v=tau, isOtherRelative(2, a)\} &
-%<0, 2, 1>\\
-%\hline
-%UA(k) ${}^{k \in \{3,12,13,21\}}$ &
-%% $\emptyset$
-%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <0, 0, 1>\\
-%\hline
-%UA(11)  &
-%% $\emptyset$
-%\{g11\} \{\} \{a11=!um(a), v=!m(a)\} & <0, 0, 0>\\
-%\hline
-%Dm(11)&
-%\{g11\},\{SG1\},\{a11=!dm(a),sg11=?m(a), v=tau, isDirectRelative(11,a)\}&<0, 0, 0>\\
-%\hline
-%DISCARD &
-%\{g11\},\{\}\{a11=DISCARD, v=tau, isOtherRelative(11,a) \}&<0, 0, 0>\\ \hline\hline
-%\end{tabular}
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <2, 0, 0>}\\
-%\hline
-%Bm(12) &
-%\{g11\} \{P12,P13\}  \{a11=a12=?bm(a), a13=!m(a), v=tau\} &
-%<2, 0, 1>\\
-%\hline
-%Bm(13) &
-%\{g11\} \{P12,P13\}  \{a11=a13=?bm(a), a12=!m(a), v=tau\} &
-%<2, 0, 1>\\
-%\hline
-%Bm(1) &
-%\{g1,g2\} \{P3\}  \{a2=a3=?bm(a), a1=!m(a), v=tau\} &
-%<0, 1, 0>\\
-%\hline
-%Um(2) &
-%\{g2\},  \{SG2\} \{a2=?bm(a), sg2=!m(a),v=tau, isOtherRelative(2, a)\} &
-%<2, 2, 0>\\
-%\hline
-%UA(k) ${}^{k \in \{3,12,13,21\}}$ &
-%% $\emptyset$
-%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <2, 0, 0>\\
-%\hline
-%UA(1)  &
-%% $\emptyset$
-%\{g1\} \{\} \{a1=!um(a), v=!m(a)\} & <0, 0, 0>\\
-%\hline
-%Um(11)&
-%\{g11\}\{SG11\}\{a11=?um(a), sg11=!m(a), v=tau, isOtherRelative(11,a)\}&<2, 0, 2>\\
-%\hline
-%DISCARD(1) &
-%\{g1\},\{\},\{a1=DISCARD, v=tau, isDirectRelative(1,a)\}&<0, 0, 0>\\
-%\hline\hline
-%\end{tabular}
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <0, 2, 0>}\\
-%\hline
-%Bm(12) &
-%\{g11\} \{P12,P13\}  \{a11=a12=?bm(a), a13=!m(a), v=tau\} &
-%<0, 2, 1>\\
-%\hline
-%Bm(13) &
-%\{g11\} \{P12,P13\}  \{a11=a13=?bm(a), a12=!m(a), v=tau\} &
-%<0, 2, 1>\\
-%\hline
-%Bm(2) &
-%\{g1,g2\} \{P3\}  \{a1=a3=?bm(a), a2=!m(a), v=tau\} &
-%<1, 0, 0>\\
-%\hline
-%Um(1) &
-%\{g1\},  \{SG1\} \{a1=?bm(a), sg1=!m(a),v=tau, isOtherRelative(2, a)\} &
-%<2, 2, 0>\\
-%\hline
-%UA(k) ${}^{k \in \{3,12,13\}}$ &
-%% $\emptyset$
-%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <0, 2, 0>\\
-%\hline
-%UA(2)  &
-%% $\emptyset$
-%\{g2\} \{\} \{a2=!um(a), v=!m(a)\} & <0, 0, 0>\\
-%\hline
-%DISCARD(2)&
-%\{g2\},\{\},\{a2=DISCARD, v=tau, isDirectRelative(2,a)\}&<0, 0, 0>\\
-%\hline
-%Um(11) &
-%\{g11\},\{SG11\}\{a11=?um(a), sg11=!m(a), v=tau, isOtherReltive(11, a) \}&<0, 2, 2>\\ \hline\hline
-%\end{tabular}
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <0, 0, 2>}\\
-%\hline
-%Bm(3) &
-%\{g1, g2\} \{P3\} \hfill \{a1=a2=?bm(a), a3=!m(a), v=tau\} &
-%<1, 1, 2>\\
-%\hline
-%DA &
-%\{g1, g2\} \{P3\} \{a1=a2=a3=?bm(a), v=?m(a)\} &
-%<1, 1, 2>\\
-%\hline
-%Um(1) &
-%\{g1\},  \{SG1\} \{a1=?bm(a), sg1=!m(a),v=tau, isOtherRelative(1, a)\} &
-%<2, 0, 2>\\
-%\hline
-%Um(2) &
-%\{g2\},  \{SG2\} \{a2=?bm(a), sg2=!m(a),v=tau, isOtherRelative(2, a)\} &
-%<0, 2, 2>\\
-%\hline
-%UA(k) ${}^{k \in \{3,12,13,21\}}$ &
-%% $\emptyset$
-%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <0, 0, 2>\\
-%\hline
-%UA(11)  &
-%% $\emptyset$
-%\{g11\} \{\} \{a11=!um(a), v=!m(a)\} & <0, 0, 0>\\
-%\hline
-%Bm(11)&
-%\{g11\},\{P12,P13\},\{a11=!m(a),a12=a13=?bm(a), v=tau, \}&<0, 0, 0>\\
-%\hline
-%DISCARD(11)&
-%\{g11\},\{\}\{a11=DISCARD, v=tau, isDirectRelative(11,a) \}&<0, 0, 0>\\ \hline\hline
-%\end{tabular}
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <1, 1, 1>}\\
-%\hline
-%UA(1)&
-%\{g1\}\{\}\{a1=!um(a),v=!m(a), isOtherRelative(1, a)\}&<0, 1, 1>\\
-%\hline
-%UA(2)&
-%\{g2\}\{\}\{a2=!um(a),v=!m(a), isOtherRelative(2, a)\}&<1, 0, 1>\\
-%\hline
-%UA(3)&
-%\{\}\{P3\}\{a3=!um(a),v=!m(a), isOtherRelative(3, a)\}&<1, 1, 1>\\
-%\hline
-%Dm(11)&
-%\{g11\}\{SG11\}\{a11=!dm(a), sg11=?m(a), v=tau, isDirectRelative(11,a)\}&<1, 1, 0>\\ \hline
-%$Dm_2(DA_2)$ &
-%\{g2\}\{SG2,P21\}\{a2=!dm(a), sg2=?m(a),a21=?bm(a), v=tau, isDirectRelative(2,a)\}&<1, 0, 1>\\ \hline
-%DISCARD(1)&
-%\{g1\} \{\} \{a1=DISCARD, v=tau, isOtherRelative(1,a)\} &
-%<0, 1, 1>\\
-%\hline
-%DISCARD(2)&
-%\{g2\} \{\} \{a2=DISCARD, v=tau, isOtherRelative(2,a)\} &
-%<1, 0, 1>\\
-%\hline
-%DISCARD(11)&
-%\{g11\} \{\} \{a11=DISCARD, v=tau, isOtherRelative(11,a)\} &
-%<1, 1, 0>\\
-%\hline\hline
-%\end{tabular}
-%\begin{tabular}{|p{2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <0, 1, 0>}\\
-%\hline
-%Bm(12) &
-%\{g11\} \{P12,P13\}  \{a11=a12=?bm(a), a13=!m(a), v=tau\} &
-%<0, 1, 1>\\
-%\hline
-%Bm(13) &
-%\{g11\} \{P12,P13\}  \{a11=a13=?bm(a), a12=!m(a), v=tau\} &
-%<0, 1, 1>\\
-%\hline
-%Um(1) &
-%\{g1\},  \{SG1\} \{a1=?um(a), sg1=!m(a),v=tau, isOtherRelative(1, a)\} &
-%<2, 1, 0>\\
-%\hline
-%Um(11) &
-%\{g11\},  \{SG11\} \{a11=?um(a), sg1=!m(a),v=tau, isOtherRelative(11, a)\} &
-%<0, 1, 2>\\
-%\hline
-%UA(k) ${}^{k \in \{3,12,13\}}$ &
-%% $\emptyset$
-%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <0, 1, 0>\\
-%\hline
-%UA(2)  &
-%% $\emptyset$
-%\{g2\} \{\} \{a2=!um(a), v=!m(a)\} & <0, 0, 0>\\
-%\hline
-%$Dm_2(DA_2)$ &
-%\{g2\},\{SG2,P21\},\{a2=!dm(a),sg2=?m(a),a21=?bm(a) v=tau, isDirectRelative(2,a)\}&<0, 0, 0>\\
-%\hline
-%DISCARD(2) &
-%\{g2\},\{\}\{a2=DISCARD, v=tau, isOtherRelative(2,a) \}&<0, 0, 0>\\ \hline\hline
-%\end{tabular}
-%\begin{tabular}{|p{2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <1, 0, 0>}\\
-%\hline
-%Bm(12) &
-%\{g11\} \{P12,P13\}  \{a11=a12=?bm(a), a13=!m(a), v=tau\} &
-%<1, 0, 1>\\
-%\hline
-%Bm(13) &
-%\{g11\} \{P12,P13\}  \{a11=a13=?bm(a), a12=!m(a), v=tau\} &
-%<1, 0, 1>\\
-%\hline
-%DISCARD &
-%\{g1\} \{\}  \{a1=DISCARD),  v=tau, isOtherRelative(1,a)\} &
-%<0, 0, 0>\\
-%\hline
-%Um(2) &
-%\{g2\},  \{SG2\} \{a2=?bm(a), sg2=!m(a),v=tau, isOtherRelative(2, a)\} &
-%<1, 2, 0>\\
-%\hline
-%Um(11) &
-%\{g11\},  \{SG11\} \{a11=?bm(a), sg11=!m(a),v=tau, isOtherRelative(11, a)\} &
-%<1, 0, 2>\\
-%\hline
-%UA(k) ${}^{k \in \{3,21\}}$ &
-%% $\emptyset$
-%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <1, 0, 0>\\
-%\hline
-%UA(1)  &
-%% $\emptyset$
-%\{g1\} \{\} \{a1=!um(a), v=!m(a)\} & <0, 0, 0>\\
-%\hline
-%$Dm_1(DA_1)$ &
-%\{g1,g11\},\{SG1, P12, P13\},\{a1=!dm(a),sg11=?m(a), a11=a12=a13=?bm(a), v=tau, isDirectRelative(1,a)\}&<0, 0, 0>\\
-%\hline
-%DA(1) &
-%\{g11\},\{P12,P13\}\{a11=a12=a13=?bm(a), v=?m(a) \}&<1, 0, 0>\\ \hline\hline
-%\end{tabular}
-%\begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <0, 1, 1>}\\
-%\hline
-%DISCARD(2) &
-%\{g2\} \{\}  \{a2=DISCARD),  v=tau, isOtherRelative(2,a)\} &
-%<0, 0, 1>\\
-%\hline
-%DISCARD(11) &
-%\{g11\} \{\}  \{a11=DISCARD),  v=tau, isOtherRelative(11,a)\} &
-%<0, 1, 0>\\
-%\hline
-%Um(1) &
-%\{g1\},  \{SG1\} \{a1=?um(a), sg1=!m(a),v=tau, isOtherRelative(1, a)\} &
-%<2, 1, 1>\\
-%\hline
-%UA(k) ${}^{k \in \{3,12,13\}}$ &
-%% $\emptyset$
-%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <0, 1, 1>\\
-%\hline
-%UA(2)  &
-%% $\emptyset$
-%\{g2\} \{\} \{a2=!um(a), v=!m(a)\} & <0, 0, 1>\\
-%\hline
-%$Dm_2(DA_2)$&
-%\{g2\},\{SG2,P21\},\{a2=!dm(a),sg2=?m(a),a21=?bm(a), v=tau, isDirectRelative(2,a)\}&<0, 0, 1>\\
-%\hline
-%Dm(11)&
-%\{g11\},\{SG11\},\{a11=!dm(a),sg11=?m(a), v=tau, isDirectRelative(11,a)\}&<0, 1, 0>\\
-%\hline\hline
-%\end{tabular}
-%
-%\noindent
-%\begin{tabular}{|p{2cm}|p{9cm}|l|}
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <0>}\\
-%\hline
-%Bm(3) &
-%\{g11\} \{P3,P12,P13,P21\} \hfill \{a11=a12=a13=a21=?bm(a), a3=!m(a), v=tau\} &
-%<1>\\
-%\hline
-%\multicolumn{2}{|l|}{Bm(12,13,21) are similar} & <1>\\
-%\hline
-%Um(11) &
-%\{g11\} \{SG11\} \{a11=?um(a), sg11=!m(a), v=tau\} & <2>\\
-%\hline
-%DA &
-%\{g11\} \{P3,P12,P13,P21\} \{a3=a11=a12=a13=a21=?bm(a), v=?m(a)\} &
-%<1>\\
-%\hline
-%UA(k) ${}^{k \in \{3,12,13,21\}}$ &
-%% $\emptyset$
-%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <0>\\
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <1>}\\
-%\hline
-%DISCARD&
-%{g11} \{\} \hfill \{a11=DISCARD, v=tau, isDirectRelative(11,a)\} &
-%<0>\\
-%\hline
-%UA(11)& \{g11\} \{\} \{a11=!um(a), v=!m(a), isOtherRelative(11,a)\}& <0>\\
-%\hline
-%UA(k) ${}^{k \in \{3,12,13,21\}}$ &
-%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <1>\\
-%\hline
-%Dm(11)& \{g11\} \{SG11\} \{a11=!dm(a), sg11=?dm(a), v=tau, isAncestor(11,a)\} & <0>\\
-%\hline\hline
-%\multicolumn{3}{|l|}{from state <2>}\\
-%\hline
-%Bm(11) &
-%{g11} \{P3,P12,P13,P21\} \hfill \{a11=!bm(a), a3=a12=a13=a21=?bm(a),
-%v=tau, isDirectRelative(11,a)\} & <0>\\
-%\hline
-%UA(11) &
-%{g11} \{\} \hfill \{a11=!um(a),
-%v=!m(a), isOtherRelative(11,a)\} & <0>\\
-%\hline
-%UA(k) ${}^{k \in \{3,12,13,21\}}$ &
-%\{\} \{Pk\} \{ak=!um(a), v=!m(a)\} & <2>\\
-%\hline
-%DISCARD &
-%{g11} \{\} \hfill \{a11=DISCARD, v=tau, isAncestor(11,a)\} & <0>\\
-%\hline\hline
-%
-%\end{tabular}
-
-\section{Open-bisimulation is compatible with closed bisimulation ?}
-
-\TODO{Underneath is the rules of the closed semantics. Not sure we
-  should keep them here, but we mentioned we should have a proof of
-  the relation between the 2 semantics... In an extended version I
-  suppose (;-)}
-
-\begin{mathpar}
-    \inferrule{\phi,\phi',\phi''\!\in\!\Phi\\s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in J}\rangle} s'\in \to\\\\
-      \phi'\!=\!\phi\!+\!\{x'_i\!\to\!V_i|x'_i\!\in\!\iv(\alpha)\land V_i\!\in\!\mathcal{D}\} \\
-      e_b\phi'\!=\!\True \\ \phi''\!=\!\phi'+\{x_j\!\to\! e_j\phi'|j\!\in\! J\}}
-    {(s,\phi) \xrightarrow{\alpha\phi'} (s',\phi'') \in\llbracket\mylangle S,s_0,
-      \to\myrangle\rrbracket_\Phi}~~{\TrUn}
-%         \end{mathpar}
-% \begin{mathpar}
-
-    \inferrule {\phi,\phi'\in\Phi\\ \alpha_l^{l\in L} \to \alpha \in \set{\symb{SV}}\\\forall i\in I\phi\setminus
-      L\phi.\,s'_i=s_i
-      \\ %\iv(\alpha)=(x_k)^{k\in K}\\\\
-      \forall l\in L\phi.\,\phi_l\in\Phi\land s_l \xrightarrow{\alpha_l\phi_l} s'_l\in\llbracket\pNet_l\rrbracket_{\Phi}\\\phi'=\phi+\uplus_{l\in L\phi} \phi_{l} }
-{\triangleleft s_i^{i\in I\phi}\triangleright \xrightarrow{\alpha\phi'} \triangleleft{s'_i}^{i\in
-        I\phi'}\triangleright  \in \llbracket\mylangle \pNet_i^{i\in I},\emptyset,\set{\symb{SV}}\myrangle\rrbracket_\Phi}~~{\bf Tr2}
-\end{mathpar}
-
-\section{Model Checking open-automata}
- \TODO{The following is about the logic formula}
-
-We want to check (and prove) properties on open pNets, using
-model-checking techniques on their open-automata. The properties will be
-expressed in any version of (action-based) branching temporal logics,
-in which we have to add constructs for quantification over the holes
-and/or leaves involved in a transition. For simplicity of the
-definition, we could choose here ACTL \cite{ACTL1990,ACTL1993} or ACTL*
-\cite{DeNicolaVaandrager95}, or the modal $\mu$-calculus
-\cite{Koz83}. Instead, for its easiness of
-expression of value-passing calculi properties, we use here the {\em
-  Model Checking Language} MCL \cite{MateescuFM2008}
-
-\begin{definition}[FH-ACTL ] The logic formula of ACTL (adding  syntax
-  for quantifying over open \pNet s : $\forall t\in {\cal{P}}, H_i \xrightarrow{a} H_i^\prime $)
-\end{definition}
-
- \begin{definition}[FH-satisfiability] Suppose that $F$ is an open
-   \pNet\ expression, and $\phi$ is a temporal logic formula, we say
-   $F$ satisfies the $\phi$, denoted as   $F\vDash_{FH} \phi$,  if
- \end{definition}
-
- In a quite standard way, we define the model checking problem as
- satisfiability of an FH-ACTL formula in a state of a FH-automaton.
-The specificity is that the model (FH-automaton) transitions include
-hypotheses about which holes are involved and predicates about their
-behaviours.
-
- \begin{definition}[The Open MC problem]
- \end{definition}
-
- \section{refinement}
- \begin{definition}[FH-refinement] FH-refinement relation $\ll$ is a
-   binary relation in between open \pNet \ expressions iff for any
-   open \pNet \ expressions $E$ and $F$, $E\ll F$, we have the
-   follows:
- \begin{itemize}
- \item $\P(E)=\P(F)$;
- \item  For any  $E\xrightarrow{S, Pred, a} E'$ based on one open transition $(S, Pred, E')$ for $F$,   there exist a set indexed by $\{j\in J\}$ of transitions  $\{ F\xrightarrow{S_j, Pred_j, a\tau^\star} F_j^\prime| a=a' up\ to\ \alpha-conversation\}$  such that $\forall j\in J, S\subset S_j,  E'\ll F_j'$ and $Pred=\cup_j Pred_j$.
- \end{itemize}
- \end{definition}
- \begin{definition}[Weak FH-refinement] FH-refinement relation $\ll$ is a binary relation in between open \pNet \ expressions iff for any open \pNet \ expressions $E$ and $F$, $E\ll F$, we have the follows:
- \begin{itemize}
- \item $\P(F)=\P(E)$;
- \item  For any  $E\xrightarrow{S, Pred, a} E'$ based on one open transition $(S, Pred, E')$ for $E$,   there exist a set indexed by $\{j\in J\}$ of transitions  $\{ F\xRightarrow{(\uplus_i S_i)_j, (\cap_i Pred_i)_j, \tau^\star a'\tau^\star} F_j^\prime| F\xrightarrow{S_i, Pred_i, a'/\tau} F_i, a=a' up \ to \ \alpha-conversation\}$  such that $\forall j\in J, S=(\uplus_i S_i)_j, E'\ll F_j^\prime$  and $Pred \subseteq \cup_j(\cap_i Pred_i)_j$.
- \end{itemize}
- \end{definition}
-
- \begin{theorem} Suppose that two \pNet s expressions $E$ and $F$ where $E$ is strong FH-bisimilar to $F$.
-For any temporal logic formula $\phi$,  if $E\vDash_{FH}\phi$, then we have $F\vDash_{FH} \phi$.
- \end{theorem}
-
-  \section{pNets Model for Hierarchical Broadcast groups  (HB-pNets): definition}\label{sec:b-pnets-def}
-
-In this section, we give the formal model for the broadcast type of
-hierarchical groups using our open parameterised networks (pNets).
-
-Hierarchical Broadcast (HB) is a way of implementing broadcasting
-algorithms within a large set of processes, with better performances
-and scalability. There have been many proposals for hierarchical
-broadcast algorithms (cite...), most of them focussing on specific
-architectures or features (in particular fault tolerance), and on
-performance analysis. Very few have given a formal description of the
-algorithm, allowing to reason about their safety properties.
-
-We give here the description of one simple HB algorithm, extracted
-from\cite{Taguchi03}, but without fault
-tolerance in a first step. For the formal description, we define a
-pNet template, that can be used as a building node in a hierarchical
-assembly of processes, organised in a tree of sub-groups; communication makes use
-of local broadcast within each sub-group, and uses gateways for
-transmission of messages, up and down, between the subgroups. The
-gateways are described as generic pLTSs, playing the role of
-``controllers'' in the pNet node.
-
-\TODO{start with a simple informal description ?}
-
-More precisely, we model a generic structure supporting
-  hierarchical groups of processes, including gateways. Then
-  we model 3 differents message
-  routing algorithms, plus 2 variants, all working on this same
-  network topology, namely:
-\begin{itemize}
-\item Full broadcast: the message goes up to the root of the
-  tree, then is broadcasted down to all processes in all groups.
-\item Hierarchical broadcast 1: similar to unicast, but within each
-  subgroup the communication uses local broadcast. Only the processes
-  in the same group than the target process will received the
-  message.
-This is the algorithm from the original paper \cite{Taguchi03}, in its
-simplified version without fault tolerance mechanisms.
-\item Hierarchical broadcast 2: same principle, but without horizontal broadcast between sibling processes and gateways: the message has to go up to the enclosing subgroup/gateway, before detecting it can go down to its target.
-\item Unicast: the gateways forward the message using the shortest
-  route in the tree. The message will reach only the specified target.
-\item Unicast 2: same principle, but with detection of sibling situations, and direct sending of messages to sibling gateways/processes, thus shortening the path in a way similar to the Hierarchical Broadcast 1.
-\end{itemize}
-
-We will use these 3 algorithms, and their variants, to illustrate the
-type of properties we can prove using open pNets and FH-bisimulations.
-Note that we cannot hope to get any strong bisimulation equivalences
-between them, the intermediate messages introduced by the protocoles
-are different. To get interesting properties, we must hide
-intermediate messages, and look for weak bisimulation properties.
-
-Here are some examples:
-
-\ERIC{Simple scenario: When hiding everything but send and receive
-  messages from processes, the resulting systems with Unicast and
-  Hierarchical broadcast are weak equivalent
-  ?}
-
-\ERIC{Hierarchical Broadcast Variants: when hiding all horizontal messages
-  the two variants are Weak Equivalent ? (same for Unicast variants) }
-
-\ERIC{What kind of relation with Full broadcast ? This is more tricky,
-on one hand we have to abstract away from the target id in the
-arguments of messages; then full broadcast is indeed broadcasting
-everywhere, so the best we can hope is some refinement relation,
-because Hierachical Broadcast has naturally less behaviours.}
-
-Given a process configuration, organised hierarchicaly in subgroups,
-it is easy to build a pNet tree reflecting the hierarchy, with the
-gateways implementing the 3 algorithms. In the next
-section, we will prove that this model of the implementation is indeed
-equivalent (modulo weak bisimulation) to a flat broadcast.
-
-\medskip
-
-The whole broadcast mechanism of hierarchical groups consists in normal
-processes, gateways and subgroups linked by gateways. Normal processes
-can send and receive messages to/from the other processes (including
-gateways) in the same group, or send up-messages to its enclosing group.
-
-\TODO{Restructure these explanations}
-A gateway has external behaviours : it sends down-messages to its associated
-subgroup, and receives up-messages from its subgroup.
-Gateways behaviour is defined by a simple pLTS with two or three states depending on the algorithm: in the
-initial state the gateway can receive a
-$?m(\widetilde{tgt})$ message (from its neighbors,
-from the enclosing group, or from its own sub-group). Then depending
-on the target address
-$\widetilde{tgt}$, it will forward the message upward as
-$!um(\widetilde{tgt})$, to its corresponding sub-group
-as $!dm(\widetilde{tgt})$, or broadcasted to all its
-neighbors in the same sub-group  as
-$!bm(\widetilde{tgt})$.
-
-\centerline{  \includegraphics[width=\linewidth]{XFIG/SchemaHB+FB}}
-\begin{figure}[h]
-%
-  \caption{Behaviour of a Gateway Broadcast controller }\label{fig:hb-gatewaybroadcast}
-\end{figure}
-
-We will describe the behaviour of the gateways in the next section,
-for the different algorithms and variants.
-
-\paragraph{Sort of the processes.}
-\label{section:processSort}
-The process parameters (the holes of the pNet structure) can emit
-messages with a target address as an argument (we abstract away from
-any other message content), or receive a message, also with the target
-address. But because of the Broadcast mechanism, there are two ways a
-process can send messages, either horizontally, broadcasted to all its
-siblings, denoted $!bm(t)$, or upward to the next hierarchy level,
-denoted $!um(t)$. In the appendix, we
-will propose a way to implement this mechanism using a small pNet as a
-filter. But from now on, this would complexify the examples, so we
-simply assume that the processes have a sort $\{?m(t), !bm(t),
-!um(t)\}$. A process is always ready to accept an incoming message,
-even if the target argument does not match with its own address. The
-filter in the appendix will be in charge of discarding misfit messages.
-
-%\begin{figure}[h]
-% \centerline{  \includegraphics[width=0.7\linewidth]{XFIG/TreeSchema.JPG}}
-%  \caption{Structure of hierarchical groups}\label{fig:tree-schema}
-% \end{figure}
-
-% \TODO{ To use ?m instead of ?bm} => done.
-
-%% \centerline{  \includegraphics[width=0.6\linewidth]{ATG/Gateway}}
-%%   \caption{Bahaviour of a Gateway controller }\label{fig:hb-gateway}
-%%  \end{figure}
-
-%% \paragraph{Variant}
-%% Another try, with a different message name for sub-group broadcast, so
-%% we do not need to pass the src id along... Not sure it makes a simpler
-%% model.
-
-%% \begin{figure}[h]
-
-%% \centerline{  \includegraphics[width=0.8\linewidth]{ATG/Gateway2}}
-%%   \caption{Bahaviour of a Gateway HB controller }\label{fig:hb-gateway2}
-%%  \end{figure}
-%% % \TODO{Eric: to draw the figs of  the broadcast and unicast of
-%% % gateway.} done
-%% \TODO{Min: to give the formal definition of address and predicates}
-
-%% \begin{figure}[h]
-%% \centerline{
-%%   \includegraphics[width=0.5\linewidth]{ATG/GatewayUnicast}
-%%   \hspace{10mm}
-%%   \includegraphics[width=0.4\linewidth]{ATG/GatewayBroadcast}}
-%%   \caption{Bahaviour of Unicast and Broadcast gateways}\label{fig:hb-gatewayunicast}
-%%  \end{figure}
-
-% \centerline{  \includegraphics[width=0.7\linewidth]{XFIG/TreeSchema.JPG}}
-
-According to the three algorithms mentioned above, we have three kinds of pNet models for Unicast, Full broadcast and Hierarchical broadcast.
-
-\begin{definition}[B-pNets]\label{B-pNets}
-A  broadcasting model is a pNet structure : \\
-\centerline{
-$B-\pNet\triangleq \mylangle gw_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}},  pc_{\widetilde{p}}^{\widetilde{p}\in \widetilde{I_P}}, sg_{\widetilde{g}}^{\widetilde{g}\in \widetilde{I_G}}, \symb{SV}\myrangle $}
-where
-\begin{itemize}
-\item[$\bullet$] $\widetilde{I_G}$ is the index set over which
-  gateways are indexed.  $gw_{\widetilde{g}}^{\widetilde{g}\in
-    \widetilde{I_G}}$ is the family of gateways. $\widetilde{I_G}$ is
-  also the set over which subgroups are indexed,
-  i.e. $gw_{\widetilde{g}}$ links $sg_{\widetilde{g}}$.
-   \begin{itemize}
-   \item Unicast: $\Sortop (gw_{\widetilde{g}})=\{?m_{\widetilde{g}}(\widetilde{tgt}), 
-   !um_{\widetilde{g}}(\widetilde{tgt}),!dm_{\widetilde{g}}(\widetilde{tgt}), ERROR_{g}\}$
-   \item Flat Broadcast: $\Sortop 
-   (gw_{\widetilde{g}})=\{?m_{\widetilde{g}}(\widetilde{tgt}), 
-   !um_{\widetilde{g}}(\widetilde{tgt}),!dm_{\widetilde{g}}(\widetilde{tgt}), 
-   ?um_{\widetilde{g}}(\widetilde{tgt})\}$
-   \item Hierarchical Broadcast: $\Sortop 
-   (gw_{\widetilde{g}})=\{?m_{\widetilde{g}}(\widetilde{tgt}), 
-   ?um_{\widetilde{g}}(\widetilde{tgt}), 
-   !um_{\widetilde{g}}(\widetilde{tgt}),!dm_{\widetilde{g}}(\widetilde{tgt}), 
-   !bm_{\widetilde{g}}(\widetilde{tgt}),DISCARD,
-       ERROR_{g}\}$
-  \end{itemize}
-\item[$\bullet$] $\widetilde{I_P}$ is the index set over which normal
-  processes are indexed.
-  \item [$\bullet$] $\widetilde{I_{G+P}} \triangleq
-    \widetilde{I_G}\uplus\widetilde{I_P}$ is the index set of all
-    subnets in a group, i.e. processes and subgroups.
-$\widetilde{I_G}$ and $\widetilde{I_P}$ must be \emph{disjoint},
-i.e. $\widetilde{I_G}\cap \widetilde{I_P}=\emptyset$. The sort of
-$pc_{\widetilde{p}}$ is
-\begin{itemize}
-\item Unicast: $\Sortop(pc_{\widetilde{p}})=\{!m_{\widetilde{p}}(\widetilde{tgt}),
-?m_{\widetilde{p}}(\widetilde{tgt})\}$
-\item Flat Broadcast: $\Sortop(pc_{\widetilde{p}})=\{!m_{\widetilde{p}},
-?m_{\widetilde{p}}\}$
-\item Hierarchical Broadcast: $\Sort(pc_{\widetilde{p}})=\{!um_{\widetilde{p}}(\widetilde{tgt}),
-?m_{\widetilde{p}}(\widetilde{tgt}),
-!bm_{\widetilde{p}}(\widetilde{tgt})\}$
-\end{itemize}
-
-\item[$\bullet$] The subgroup $sg_{\widetilde{g}}$ can be taken the hole of open pNets 
-which can be inserted the sub-pNets(subgroups) and has the sort: $\Sortop 
-(sg_{\widetilde{g}})=\{?m_{\widetilde{g}}(\widetilde{t}), 
-!m_{\widetilde{g}}(\widetilde{t})\}$;
-
-\item[$\bullet$]$\symb{SV}$ is a set of synchronisation vectors. For
-  the $HB-\pNet$ node,  we have six kinds of ``normal'' synchronisation
-  vectors in the model, plus 2 ``error'' vectors, listed in
-  Fig. \ref{fig:HBvectors}.
-
-\end{itemize}
-\end{definition}
-
-\centerline{  \includegraphics[width=0.85\linewidth]{ATG/GatewayHB}}
-
-\centerline{
-   \includegraphics[width=0.5\linewidth]{ATG/GatewayUnicast}
-   \hspace{10mm}
-   \includegraphics[width=0.4\linewidth]{ATG/GatewayBroadcast}}
-
-%% \vskip 0.5cm
-%% \begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%% \hline\hline
-%% \multicolumn{3}{|l|}{Full broadcasting}\\
-%% \hline
-%% $(UC)_{\widetilde{k}}$ & $
-%%      \symb{sv}_{u(\widetilde{i}.k)}\triangleq
-%%      <?um_{\widetilde{i}.k}(\widetilde{t})\shortotimes
-%%      -^{\widetilde{I_P}}\shortotimes
-%%      !m_{\widetilde{i}.k}(\widetilde{t})\shortotimes
-%%      -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
-%%          k\}}}>\longrightarrow \tau(
-%%      m_{\widetilde{i}.k}(\widetilde{t}))$ & $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}$\\
-%% \hline
-%% $(DM )_{\widetilde{k}}$& $\symb{sv}_{?\widetilde{i}}\triangleq
-%%      <?m_{\widetilde{i}.k}(\widetilde{t})\shortotimes
-%%      -^{\widetilde{I_{G+P}}
-%%       \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\shortotimes -^{\widetilde{I_G}}>\longrightarrow
-%%      ?m_{\widetilde{i}}(\widetilde{t})$&$\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}\uplus \widetilde{I_P}$\\
-%%      \hline
-%% $(UM)_{\widetilde{k}}$&
-%% $\symb{sv}_{!\widetilde{i}}\triangleq
-%%     <!um_{\widetilde{i}.k}(\widetilde{t})\shortotimes
-%%     -^{\widetilde{I_P}\uplus
-%%       \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\shortotimes
-%%     -^{\widetilde{I_G}}>\longrightarrow
-%%     !m_{\widetilde{i}.k}(\widetilde{t})$ & $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}\uplus \widetilde{I_P}$\\
-
-%% \hline
-%% $(DG )$&
-%% $\symb{sv}_{?\widetilde{i}}\triangleq
-%%      <?m_{\widetilde{i}.k}^{\forall k\in
-%%        I_K}(\widetilde{t})\shortotimes
-%%      -^{\widetilde{I_P}}\shortotimes -^{\widetilde{I_G}}>\longrightarrow
-%%      ?m_{\widetilde{i}}(\widetilde{t})$ & $I_K = \{k/\widetilde{i}.k\in \widetilde{I_G}\uplus
-%% \widetilde{I_P}\}$\\
-
-%% \hline\hline
-%% \end{tabular}
-%% \vskip 0.5cm
-
-%% \begin{tabular}{|p{2.2cm}|p{9cm}|l|}
-%% \hline\hline
-%% \multicolumn{3}{|l|}{Unicast broadcasting}\\
-%% \hline
-%% $(UC)_{\widetilde{k}}$ & $
-%%      \symb{sv}_{u(\widetilde{i}.k)}\triangleq
-%%      <?um_{\widetilde{i}.k}(\widetilde{t})\shortotimes
-%%      -^{\widetilde{I_P}}\shortotimes
-%%      !m_{\widetilde{i}.k}(\widetilde{t})\shortotimes
-%%      -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
-%%          k\}}}>\longrightarrow \tau(
-%%      m_{\widetilde{i}.k}(\widetilde{t}))$ & $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}$\\
-%% \hline
-%% $(DM )_{\widetilde{k}}$& $\symb{sv}_{?\widetilde{i}}\triangleq
-%%      <?m_{\widetilde{i}.k}(\widetilde{t})\shortotimes
-%%      -^{\widetilde{I_P}\uplus
-%%       \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\shortotimes -^{\widetilde{I_G}}>\longrightarrow
-%%      ?m_{\widetilde{i}}(\widetilde{t})$&$\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}\uplus \widetilde{I_P}$\\
-%%      \hline
-%%      $(UM)_{\widetilde{k}}$&
-%% $\symb{sv}_{!\widetilde{i}}\triangleq
-%%     <!um_{\widetilde{i}.k}(\widetilde{t})\shortotimes
-%%     -^{\widetilde{I_P}\uplus
-%%       \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\shortotimes
-%%     -^{\widetilde{I_G}}>\longrightarrow
-%%     !m_{\widetilde{i}.k}(\widetilde{t})$ & $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}\uplus \widetilde{I_P}$\\
-%% \hline
-%% $(DK)_{\widetilde{k}}$&
-%% $\symb{sv}_{!\widetilde{i}}\triangleq
-%%     <!m_{\widetilde{i}.k}(\widetilde{t})\shortotimes
-%%     ?m_{\widetilde{i}.g}(\widetilde{t})\shortotimes -^{\widetilde{I_P}\uplus
-%%       \widetilde{I_G}\backslash\{\widetilde{i}\cdot k,\widetilde{i}\cdot g\}}\shortotimes
-%%     -^{\widetilde{I_G}}>\longrightarrow
-%%     \tau(m_{\widetilde{i}.k}(\widetilde{t}))$ & $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}\uplus \widetilde{I_P}$\\
-
-%% \hline\hline
-%% \end{tabular}
-%\end{definition}
-
-%
-%  \begin{itemize}
-%  \item[$(BG)_{\widetilde{k}}$]
-%    $\symb{sv}_{b(\widetilde{i}.k)}\triangleq
-%    <?m_{\widetilde{i}.j}^{\forall j\in I_K}(\widetilde{t})
-%    \shortotimes !bm_{\widetilde{i}.k}(\widetilde{t})
-%    \shortotimes -^{\widetilde{I_G}}>\longrightarrow \tau( bm(\widetilde{t}))$,
-%where $I_K = \{k/\widetilde{i}.k\in \widetilde{I_G}\uplus
-%\widetilde{I_P}\}$, and $\widetilde{k}=\widetilde{i}.k$
-%
-%  \item [$(UM)_{\widetilde{k}}$] $
-%    \symb{sv}_{!\widetilde{i}}\triangleq
-%    <!um_{\widetilde{i}.k}(\widetilde{t})\shortotimes
-%    -^{\widetilde{I_P}\uplus
-%      \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\shortotimes
-%    -^{\widetilde{I_G}}>\longrightarrow
-%    !m_{\widetilde{i}.k}(\widetilde{t})$,
-%where $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}\uplus \widetilde{I_P}$;
-%
-%   \item [$(DC)_{\widetilde{k}}$] $
-%     \symb{sv}_{d(\widetilde{i}.k)}\triangleq
-%     <!dm_{\widetilde{i}.k}(\widetilde{t})\shortotimes
-%     -^{\widetilde{I_P}}\shortotimes
-%     ?m_{\widetilde{i}.k}(\widetilde{t})\shortotimes
-%     -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}}
-%     >\longrightarrow
-%     \tau(m_{\widetilde{i}.k}(\widetilde{t}))$,
-%where $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}$;
-%
-%   \item [$(UC)_{\widetilde{k}}$] $
-%     \symb{sv}_{u(\widetilde{i}.k)}\triangleq
-%     <?um_{\widetilde{i}.k}(\widetilde{t})\shortotimes
-%     -^{\widetilde{I_P}}\shortotimes
-%     !m_{\widetilde{i}.k}(\widetilde{t})\shortotimes
-%     -^{{\widetilde{I_G}\backslash\{\widetilde{i}\cdot
-%         k\}}}>\longrightarrow \tau(
-%     m_{\widetilde{i}.k}(\widetilde{t}))$,
-%where $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}$;
-%
-%   \item [$(DG )$] $\symb{sv}_{?\widetilde{i}}\triangleq
-%     <?m_{\widetilde{i}.k}^{\forall k\in
-%       I_K}(\widetilde{t})\shortotimes
-%     -^{\widetilde{I_P}}\shortotimes -^{\widetilde{I_G}}>\longrightarrow
-%     ?m_{\widetilde{i}}(\widetilde{t})$,
-%where $I_K = \{k/\widetilde{i}.k\in \widetilde{I_G}\uplus
-%\widetilde{I_P}\}$.
-%
-% \item [$(DM )_{\widetilde{k}}$] $\symb{sv}_{?\widetilde{i}}\triangleq
-%     <?m_{\widetilde{i}.k}(\widetilde{t})\shortotimes
-%     -^{\widetilde{I_P}\uplus
-%      \widetilde{I_G}\backslash\{\widetilde{i}\cdot k\}}\shortotimes -^{\widetilde{I_G}}>\longrightarrow
-%     ?m_{\widetilde{i}}(\widetilde{t})$,
-%where $\widetilde{k}=\widetilde{i}.k\in \widetilde{I_G}\uplus \widetilde{I_P}$;
-%
-%\item [$(DIS)_{\widetilde{k}}$] $\symb{sv}_{dc}\triangleq
-%     <DISCARD_{\widetilde{i}.k}^{\forall k\in
-%       I_K}(\widetilde{t})\shortotimes
-%     -^{\widetilde{I_P}}\shortotimes -^{\widetilde{I_G}}>\longrightarrow
-%     \tau(m_{\widetilde{i}.k}(\widetilde{t}))$,
-%where $I_K = \{k/\widetilde{i}.k\in \widetilde{I_G}\uplus
-%\widetilde{I_P}\}$.
-%\end{itemize}
-%\end{itemize}
-
-\medskip
-
-   \begin{example}
-We sketch here one example showing how to send one message from one
-process in one group to the other process in the other group by using
-broadcast mechanism of Hierarchical groups in {\sl HB-pNets}. Here we
-use 12, 122,... instead of the denotation above 1.2 , 1.2.2,... in the
-definition for short.
-   \end{example}
-
-\begin{figure}[h]
-  \includegraphics[width=1.0\linewidth]{ATG/Inst5}
-  \caption{A Hierarchical Broadcast pNet Structure }\label{fig:hb-structure}
- \end{figure}
-
-In Fig.~\ref{fig:hb-structure}, suppose that one root group $G$ has
-  two gateways $g_1$ and $g_2$ which link two subgroups $G_1$ and
-  $G_2$, and a normal process $P_3$. Subgroup $G_1$ has one gateway $g_{12}$ which links the
-  subsubgroup $G_{12}$ one normal process $P_{12}$.
-  $G_2$ and $G_{11}$ have two normal processes respectively.
-
-The procedure of sending one message from process $P_{21}$ to process
-$P_{122}$ can be described as follows:
-
-\TODO{To be written, unless it is already in a previous section ?}
-
-\section{Computing the open operational semantics}
-
-In this section we show how to unfold the operational semantic rules
-on our hierarchical broadcast example, compute open transitions, and
-start building the open automaton.
-
-The sketch we give here considers one particular pNet node, with 2
-subgroups, and a specific number of processes in each root- and sub-
-groups. Also we make some hypotheses on the sorts of the processes.
-Clearly the full proof will have to deal with generalisations of this
-particular case.
-
-% \newcommand{\NetS}[1]{\symb{\guillemotleft} #1 \symb{\guillemotright}}
-
-%% A transition in the proof tree is either :
-%% \begin{itemize}
-%% \item a transition in a pLTS, with eventually a state change.
-%% \item an action in the sort of a Hole.
-%% \item the ``global action'' resulting from a synchronisation vector in the pNet.
-%% \end{itemize}
-
-%% \begin{figure}[h]
-%% $\NetS{0_{g1}, 0_{g2}, \sm{P3}, \NetS{0_{g11}, \sm{P12}, \sm{P13},
-%%       \sm{SG11}}, \NetS{\sm{P21}, \sm{P22}}}$
-%% \hfill
-%% $<<0_{g1}, 0_{g2}, 0_{g11}>>$
-
-%% \caption{initial state of our example, and state of the corresponding Expr}
-%% \end{figure}
-
-For each possible synch vector of the root node, we build a proof
-tree. From each such proof tree we derive a {\em open transition},
-representing a symbolic transition in the open automaton
-of the pNet.
-%% Now we compute the corresponding open-transition, getting rid of the
-%% intermediate deduction steps, keeping only premisses for the pLTS
-%% and holes involved, and the predicate.
-
-%% \begin{mathpar}
-%%   \inferrule
-%%       {0_{gw2} \xrightarrow{a_{gw2}} 2_{gw2} \\
-%%            \xrightarrow{b_{P21}}
-%%            \\ Pred_{Root}
-%%       }
-%%            {\ostate{000} \xrightarrow{v} \ostate{020}}
-%%       ~~ [UG\_2(UM\_21)]
-%% \end{mathpar}
-
-\medskip
-Following the residual algorithm from section \ref{sec:xxx}, we can
-build the full open-automaton of our pNet. We give here in Figure
-\ref{fig:xxx} only a small view of its first two states.
-
-\paragraph{Proving equivalences}
-
-We present a (partial) set of transitions of our two processes in the
-following tables. For each state of the expression, we have a set of
-lines, each defining one open transition starting from this state.
-For each specific+ation rule, we show the vectors used to prove it, the
-formal hypothesis and the predicte, and the resulting expression
-state.
-
-The resulting LTS for our example is shown in Fig. \ref{fig:HB-lts}.
-
-\begin{figure}[h]
-\includegraphics[width=9cm]{ATG/FullLTS}
-
-\caption{(symbolic) behaviour of the example, Hierarchical version}
-\label{fig:HB-lts}
-\end{figure}
-
-For the flattened version, the computation of the symbolic graph is similar, but of course simpler. The result is shown in Fig. \ref{fig:Flat-lts}.
-
-\begin{figure}[h]
-\includegraphics[width=9cm]{ATG/FlatLTS}
-
-\caption{(symbolic) behaviour of the example, Flat version}
-\label{fig:Flat-lts}
-\end{figure}
-
-%%% REVISION: what we did:
-%%% added the notation (x|-> J) page 3 (used to define composition)
-%%% defined pnet composiiton (filling a hole)
-%%% defined pnests bisimilarity (trivial)
-%%% added constraint on synchronisation vector: no fresh variable in target action
-%%% changed Pred def: iff instead of implies

### 2019-11-14 2016-Weak-FH-Bisim/WeakBisim.tex
Deux dessins en ATG

@@
 
-Finaly, we list here, in raw format, the 12 OTs computed by the tool:
+Finaly, we list here, in raw format, the 12 OTs computed by the tool
+\TODO{BUG! We should have 19 OTs...}:
 
@@
 \end{lstlisting}
+
+And here is a  drawing of this open automaton, slightly simplified for readability:
+
+\begin{figure}[h]
+  \centerline{\includegraphics[width=10cm]{ATG/SPImplOpen}}
+  \caption{Open Automaton of the Simple Protocol Implementation}  \label{SimpleProtCounter:ImplOA}
+\end{figure}
+
+And a partially saturated Automaton:
+
+\begin{figure}[h]
+  \centerline{\includegraphics[width=13cm]{ATG/SPImplWeakOpen}}
+  \caption{Weak Open Automaton, partial}  \label{SimpleProtCounter:ImplWOA}
+\end{figure}
 

### 2019-11-17 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf. paper: Typo.
actions can have action subterms
corrected a couple of typos

@@
 $\mathcal{A}_\P$, with $\mathcal{A}_\P\subseteq\mathcal{T}_\P$.
-\QIN{As action expressions $\mathcal{A}_\P$ we built will not be used to present data terms, we have} 
-$\mathcal{E}_\P\cap\mathcal{A}_\P=\emptyset$;
- action terms will use data expressions as sub-terms.
+%% \QIN{As action expressions $\mathcal{A}_\P$ we built will not be used to present data terms, we have} 
+%% $\mathcal{E}_\P\cap\mathcal{A}_\P=\emptyset$;
+ \ERIC{Action terms can use both data and action expressions as sub-terms}.
 The function $\vars(t)$ identifies the set of variables in a term
@@
 Also, the accuracy of a `SAT' result may depend on the characteristics of the specific theory used to axiomatise the data domains and operators.
-Such theories may be intrinsically undecidable, or may not properly handled by the SMT engine (e.g.
+Such theories may be intrinsically undecidable, or may not  be properly handled by the SMT engine (e.g.
 for recursive datatypes).
-However, while building the open automaton, that is a symbolic representation of the pNet behavior, it is not logically incorrect to keep potentially unsatisfiable transitions, so we will treat undecidable results, and time bounds failures, as SAT.
+However, while building the open automaton, which is a symbolic representation of the pNet behavior, it is not logically incorrect to keep potentially unsatisfiable transitions, so we will treat undecidable results, and time bounds failures, as SAT.
 So the open automaton may have more transitions and states than the theoretical minimum.}
@@
                             \xrightarrow{acc(x_2)}_Q \},~
-                                        v=0,~
+                                        [v=0],~
                                         \{v\gets 1\}}

### 2019-11-18 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf paper: Modifications and replies to reviewers by Simon: - 1 in the introduction re lack in previous work on BIP architectures - 1 in the conclusion re scalability

@@
 \newcommand{\coloncolon}{{:\hspace{-.2ex}:}}
+\definecolor{darkgreen}{rgb}{0.2, 0.55, 0.2}
+\newcommand{\Simon}[1]{\textcolor{darkgreen}{#1}}
 
@@
 property, the resulting system satisfies their conjunction.
-
-But the interaction feature in architectures does not handle
+%
+\Simon{However, \cite{AttieBBJS16-architectures-faoc} did not provide
+  any mechanism for verifying the correctness of individual
+  architectures.  The encoding presented in this paper provides such a
+  mechanism.}
+
+\st{But the interaction feature in architectures does not handle
 data-sensitive interaction constraints. Using an encoding of
@@
 pNets was an interesting alternative to a direct extension to the
-architecture semantics.
+architecture semantics.}
 
@@
 
-We validate the approach on two larger examples, 
+We validate the approach on \Simon{a larger example}\st{two larger examples}, 
 based on a BIP architecture taken from an earlier nanosatellite case
-study~\cite{CubETH-case-study}. We also show how such architectures
+study~\cite{CubETH-case-study}.  \Simon{This example shows that
+open-automata-based semantics can be instrumental in verifying the
+properties enforced by the architectures through an encoding into open
+pNets.
+In order to evaluate the potential
+%
+of our approach to scale to larger systems, we also apply the proposed
+techniques to a BIP architecture obtained by combining two instances
+of the Failure Monitor architecture.  Our results show that, even
+though, the performance of the smart algorithm degrades more than
+linearly, execution times remain reasonably small.  It should be noted
+that the aim of our approach, particularly in the case of BIP
+architectures, is to allow symbolic verification of design patterns to
+show that they do impose corresponding properties. Safety of the system is obtained compositionally, whereas liveness is verified by checking \emph{pair-wise} non-interference.
+%
+}\st{We also show how such architectures
 can be composed, and how our approach scales.
@@
 We also compare the practical performances of the two algorithms and
-show the benefit gained using the smart approach.
+show the benefit gained using the smart approach.}
 

### 2019-11-19 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf paper: - Added the discussion in the last paragraph of the conclusion re architecture styles - Moved the mention of the Coordination 2019 paper (architectures with data) to that same paragraph (otherwise not clear why mention them)

@@
 
-\ERIC{The original specification of the nanosatellite software, using BIP architecture patterns, was handling data in the BIP components behavior, but was not able to use data in the synchronisation between components.
-We have shown in \cite{BHM19:Coordination} how to overcome this limit, allowing data constraints in BIP architecture connectors, and providing an encoding of such architectures in terms of open pNets.}
+\ERIC{\st{The original specification of the nanosatellite software, using BIP architecture patterns, was handling data in the BIP components behavior, but was not able to use data in the synchronisation between components.
+We have shown in \cite{BHM19:Coordination} how to overcome this limit, allowing data constraints in BIP architecture connectors, and providing an encoding of such architectures in terms of open pNets.}}
 
@@
 
+\Simon{The results presented in this paper open a number of avenues
+  for future work.}
+%
 Naturally, our next goals after the generation of the open automata
@@
 will be the basis for comparing open transitions.
+
+\Simon{BIP architectures in this paper and in the CubETH case study \cite{CubETH-case-study} involved data in the BIP components behaviour but not in the interactions among components.
+We have shown in \cite{BHM19:Coordination} how to overcome this limit, allowing data transfer in BIP architecture connectors and providing an encoding of such architectures in terms of open pNets.
+To push the study of BIP architecture verification using open pNets even further, one can observe that there is a certain ``regularity'' in the structure of the composed architecture in Figure~\ref{schema:ArchFailure:BIP:Double}.
+Indeed, both architectures in Figures~\ref{schema:ArchFailure:BIP} and \ref{schema:ArchFailure:BIP:Double} are instances of the same \emph{architecture style} \cite{MBBS16-diagrams} for 1 and 2 monitored processes, respectively.
+The question then naturally arises of whether some version of open pNets (\eg extended to accommodate a parameterised number of sub-pNets) can be used to verify certain architectural styles without instantiating them with fixed parameter values.
+Although this problem is know to be undecidable in the general case (see, \eg \cite{KKW+16-foil-concur}), it would be interesting to study the interplay of existing techniques, such as well structured transition systems \cite{WSTSE!}, with open pNet extensions.}
 

### 2019-11-19 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf. paper: Typos.

--- 2019-11-18 2017-Xudong-SMT/ActaInformatica.tex
@@
 
-\ERIC{This shows an example of the generic ``FUN'' constructor used to construct expressions (of the Action sort, or of any data sort) in any algebra presentations.
+\ERIC{This shows an example of the generic $\texttt{FUN}$ constructor used to construct expressions (of the Action sort, or of any data sort) in any algebra presentations.
   Here \texttt{FUN} will be instanciated e.g. as, $\delta(x)$ in the form of $\texttt{FUN}_{Action, Data}(\delta, x)$ where $x$ is a variable of type $Data$.
@@
 a_1\neq \delta(y_1)]$.
-It denotes a possible behavior of $P>>Q$, for any possible action of the hole $P$ that respects the vector predicate, that is, any action that does not match $\delta(y_1)$, for any value of the variable $y_1$.
+It denotes a possible behaviour of $P>>Q$, for any possible action of the hole $P$ that respects the vector predicate, that is, any action that does not match $\delta(y_1)$, for any value of the variable $y_1$.
 Remark that the data-oriented encoding in pNet $EnableData$ has the same synchronisation vectors, up to the usual alpha conversion. Only the controller $CState$ has been replaced by $CData$.
@@
           [v_1=0 \land v_2 = 0 \land \forall y_1. acc(x_2) \neq
-            \delta(y_1)] ~~ \{v_1:=1\}
+            \delta(y_1)] ~~ \{v_1\leftarrow1\}
         }
@@
         state space of this version is reduced to $\ostate{0,0}$, and
-        the state change is replaced by the assignment ``$v_1:=1$''.
+        the state change is replaced by the assignment ``$v_1\leftarrow1$''.
 
@@
 \QIN{The matching would also fail if the active actions in the vector and the active behaviours in the chosen combination are not matched by pattern-matching or unification.
-Such case will be checked later, together with the guards collected from synchronisation vectors and from PLTS transtions, using the satisfiability check in the SMT engine.}
+Such case will be checked later, together with the guards collected from synchronisation vectors and PLTS transitions, using the satisfiability check in the SMT engine.}
 
@@
 for recursive datatypes).
-However, while building the open automaton, which is a symbolic representation of the pNet behavior, it is not logically incorrect to keep potentially unsatisfiable transitions, so we will treat undecidable results, and time bounds failures, as SAT.
+However, while building the open automaton, which is a symbolic representation of the pNet behaviour, it is not logically incorrect to keep potentially unsatisfiable transitions, so we will treat undecidable results, and time bounds failures, as SAT.
 So the open automaton may have more transitions and states than the theoretical minimum.}
@@
 
-Here the behavior of the hole ``$P$'' ($a_1$ in Example~\ref{schema:unsat-ot}), after matching with the synchronisation vectors, appears as a variable
+Here the behaviour of the hole ``$P$'' ($a_1$ in Example~\ref{schema:unsat-ot}), after matching with the synchronisation vectors, appears as a variable
 ``|a1:sva\_SVA0:15:1|'', and ``$R$'' ($acc(x_2)$) as ``|(ACT delta
@@
 controllers from Figure~\ref{schema:enable-pnets}, their nature is very
-different: they represent the behavior of the whole system, including
+different: they represent the behaviour of the whole system, including
 the holes $P$ and $Q$. Their transitions do not rely on a particular
@@
 
-\ERIC{The original specification of the nanosatellite software, using BIP architecture patterns, was handling data in the BIP components behavior, but was not able to use data in the synchronisation between components.
+\ERIC{The original specification of the nanosatellite software, using BIP architecture patterns, was handling data in the BIP components behaviour, but was not able to use data in the synchronisation between components.
 We have shown in \cite{BHM19:Coordination} how to overcome this limit, allowing data constraints in BIP architecture connectors, and providing an encoding of such architectures in terms of open pNets.}

### 2019-11-19 2017-Xudong-SMT/ActaInformatica.tex

@@
 
-\ERIC{The original specification of the nanosatellite software, using BIP architecture patterns, was handling data in the BIP components behaviour, but was not able to use data in the synchronisation between components.
-We have shown in \cite{BHM19:Coordination} how to overcome this limit, allowing data constraints in BIP architecture connectors, and providing an encoding of such architectures in terms of open pNets.}
+\ERIC{\st{The original specification of the nanosatellite software, using BIP architecture patterns, was handling data in the BIP components behavior, but was not able to use data in the synchronisation between components.
+We have shown in \cite{BHM19:Coordination} how to overcome this limit, allowing data constraints in BIP architecture connectors, and providing an encoding of such architectures in terms of open pNets.}}
 

### 2019-11-19 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf paper: - revised the reply regarding the refinement of the Failure Monitor architecture (now footnote 2 in Section 5.2) - provided corresponding short answers to the reviewers

--- 2019-11-19 2017-Xudong-SMT/ActaInformatica.tex
@@
 
-In this section, we present the Failure Monitor architecture from the
+In this section, we present \Simon {a variation of} the Failure Monitor architecture from the
 CubETH nanosatellite on-board software
@@
 
-\ERIC{\st{The original specification of the nanosatellite software, using BIP architecture patterns, was handling data in the BIP components behavior, but was not able to use data in the synchronisation between components.
-We have shown in \cite{BHM19:Coordination} how to overcome this limit, allowing data constraints in BIP architecture connectors, and providing an encoding of such architectures in terms of open pNets.}}
-
-Figure~\ref{schema:ArchFailure:BIP} shows this refined version of the
-Failure Monitor architecture used in~\cite{CubETH-case-study}.
+Figure~\ref{schema:ArchFailure:BIP} shows this modified version of the
+Failure Monitor architecture used in~\cite{CubETH-case-study}.\footnote{%
 %
-The architecture consists of 2 \emph{coordinator components}
+  \Simon{%
+  The original CubETH case study \cite{CubETH-case-study} focused on
+  the possibility of assembling a model of a complex software system
+  in a systematic way by applying architectures to discharge
+  individual system requirements.  Here, we are more interested by the
+  properties of the Failure Monitor architecture by itself.  For that
+  reason, we provide a modified version, in particular decomposing the
+  coordinator into a Controller and a Timer, altering them to allow
+  more flexibility in the acceptable behaviours.  In other words, this
+  modification enforces essentially the same properties, while
+  discarding less acceptable behaviours.
+  }
+%
+} The architecture consists of 2 \emph{coordinator components}
 ($\NameCtrl$ and $\NameTimer$, for \emph{Control} and \emph{Timer},

### 2019-11-19 2017-Xudong-SMT/ActaInformatica.tex
Updated the justification of the liveness property (end of Section 5.2)

@@
 The satisfaction of the liveness property relies on the observation
-that in the state $\ostate{s2,t0}$ only the reset transition involves
-$\NameCtrl$.  Therefore, under resonable scheduling assumptions,
-$\PortReset$ will always be fired.
+that \Simon{the only loop starting in the state $\ostate{s1,t1}$ and involving neither $\mathit{reset}$, nor $\mathit{resume}$ or $\mathit{ask}$, is the self-loop $\mathit{fail(b0)}$.
+By further inspecting the synchronisation vector $SV0$, we observe that this self-loop corresponds to the transitions $\mathit{fail(false)}$ and $\mathit{start(false)}$ in the two pLTSs.
+Recall that these transitions (carrying the value $\mathit{false}$) are introduced by the encoding.
+That is, none of the two coordinating components are involved in the joint transition.
+Therefore, under resonable scheduling assumptions,
+the transition $\mathit{ask}$ will eventually be fired.}
 

### 2019-11-19 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf. paper: Adjust the position of the table in Sect.5.4 to reduce the blank in the middle of page 25.

@@
 \ERIC{Each call to the SMT engine will return either SAT or UNSAT results, or may fail due to time bounds.
-Also, the accuracy of a `SAT' result may depend on the characteristics of the specific theory used to axiomatise the data domains and operators.
+Also, the accuracy of a ``SAT'' result may depend on the characteristics of the specific theory used to axiomatise the data domains and operators.
 Such theories may be intrinsically undecidable, or may not  be properly handled by the SMT engine (e.g.
@@
 Eclipse Equinox, with Java 1.8.
+
+In the basic cases ($EnableState$, $EnableData$) there is no
+benefit, and even an overhead in the case of $EnableData$,
+because of the extra step of checking SAT at the end of the
+algorithm.
+
+But as soon as there are more OTs in the system and not all
+states are reachable, these tests show a significant benefit of the ``smart'' strategy, in
+the considered use-cases, with 50\% of time saving for the $FailureTimer$,
+over to 80\% for the composition, depending
+on the nature of the examples, but increasing significantly
+with their complexity.
 
@@
 \medskip
-        In the basic cases ($EnableState$, $EnableData$) there is no
-        benefit, and even an overhead in the case of $EnableData$,
-        because of the extra step of checking SAT at the end of the
-        algorithm.
-But as soon as there are more OTs in the system and not all
-states are reachable, these tests show a significant benefit of the ``smart'' strategy, in
-the considered use-cases, with 50\% of time saving for the $FailureTimer$,
-over to 80\% for the composition, depending
-        on the nature of the examples, but increasing significantly
-        with their complexity.
 

### 2019-11-19 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf. paper: Typos in Sect.4.5.
|(ACT delta |x:sva_SV4:1:2| -> (ACT delta |x:sva_SV4:1:2|)

@@
 Here the behaviour of the hole ``$P$'' ($a_1$ in Example~\ref{schema:unsat-ot}), after matching with the synchronisation vectors, appears as a variable
-``|a1:sva\_SVA0:15:1|'', and ``$R$'' ($acc(x_2)$) as ``|(ACT delta
-|x:sva\_SV4:1:2|''. Line 16 requires that $a_1 = \delta(x_2)$ to match
+``|a1:sva\_SVA0:15:1|'', and ``$R$'' ($acc(x_2)$) as ``(ACT delta
+|x:sva\_SV4:1:2|)''. Line 16 requires that $a_1 = \delta(x_2)$ to match
 the second synchronisation vector of the root pNet node, and lines
@@
 case-study~\cite{CubETH-case-study} realised using BIP.
+
 The architecture-based design process in BIP takes as input a set of

### 2019-11-19 2017-Xudong-SMT/ActaInformatica.tex
Update ActaInformatica.tex

@@
 well-formedness of a pNet system, and to define the translation of the pNet
-semantics into the SMT engine input language (\cite{BarFT-RR-17}).
+semantics into the SMT engine input language (see \cite{BarFT-RR-17}).
 

### 2019-11-19 2017-Xudong-SMT/ActaInformatica.tex
final versino ??

--- 2019-11-19 2017-Xudong-SMT/ActaInformatica.tex
@@
 \newcommand{\NOTE}[1]{\textcolor{blue}{\textbf{[NOTE:#1]}}}
-\newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
 \newcommand{\OTvar}{\texttt}
@@
 \definecolor{airforceblue}{rgb}{0.26, 0.44, 0.56}
-\newcommand{\QIN}[1]{\textcolor{airforceblue}{#1}}
 \newcommand{\coloncolon}{{:\hspace{-.2ex}:}}
 \definecolor{darkgreen}{rgb}{0.2, 0.55, 0.2}
-\newcommand{\Simon}[1]{\textcolor{darkgreen}{#1}}
+%\newcommand{\Simon}[1]{\textcolor{darkgreen}{#1}}
+%\newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
+%\newcommand{\QIN}[1]{\textcolor{airforceblue}{#1}}
+%\newcommand{\YX}[1]{{\color{red}#1}}
+\newcommand{\Simon}[1]{{#1}}
+\newcommand{\ERIC}[1]{{#1}}
+\newcommand{\QIN}[1]{{#1}}
+\newcommand{\YX}[1]{{#1}}
 
@@
 
-\newcommand{\YX}[1]{{\color{red}#1}}
-
 % Volume frontmatter
@@
 
-\st{But the interaction feature in architectures does not handle
-data-sensitive interaction constraints. Using an encoding of
-architectures, extended with data-dependent interactions, into open
-pNets was an interesting alternative to a direct extension to the
-architecture semantics.}
+%% \st{But the interaction feature in architectures does not handle
+%% data-sensitive interaction constraints. Using an encoding of
+%% architectures, extended with data-dependent interactions, into open
+%% pNets was an interesting alternative to a direct extension to the
+%% architecture semantics.}
 
@@
 
-We validate the approach on \Simon{a larger example}\st{two larger examples}, 
+We validate the approach on \Simon{a larger example},%\st{two larger examples}, 
 based on a BIP architecture taken from an earlier nanosatellite case
@@
 architectures, is to allow symbolic verification of design patterns to
-show that they do impose corresponding properties. Safety of the system is obtained compositionally, whereas liveness is verified by checking \emph{pair-wise} non-interference.
+show that they do impose corresponding properties.
+Safety of the system is obtained compositionally, whereas liveness is verified by checking \emph{pair-wise} non-interference.
+In both cases, the main characteristic of the approach is compsitionality, so we can compute the behavior and analyse the properties on \emph{small open systems}, and use these properties independently when composing bigger systems.
 %
-}\st{We also show how such architectures
-can be composed, and how our approach scales.
-This example shows that
-open-automata-based semantics can be instrumental in verifying the
-properties enforced by the architectures through an encoding into open
-pNets.
-We also compare the practical performances of the two algorithms and
-show the benefit gained using the smart approach.}
+}
+%% \st{We also show how such architectures
+%% can be composed, and how our approach scales.
+%% This example shows that
+%% open-automata-based semantics can be instrumental in verifying the
+%% properties enforced by the architectures through an encoding into open
+%% pNets.
+%% We also compare the practical performances of the two algorithms and
+%% show the benefit gained using the smart approach.}
 
@@
 application of Tr2 have to be fresh and all distinct.
+
+The reader may notice that the structure of OTs produced by these rules is richer than the one from the definitions in Section \ref{def:OpenTransitions}, as they contain information about the leaves transitions in each OT.
+This is also the case in the implementation, and provides us with tracability and debugging features in the tool.
 

### 2019-11-19 2017-Xudong-SMT/ActaInformatica.tex
Adjust the position of table on page 25.
a couple of typos fixed

@@
 Such synchronised actions do not play any special role for defining the semantics of pNets, but as one can expect, they will be crucial for defining weak equivalences.
-The pNet can be given as follow:
+The pNet can be given as follows:
 \begin{itemize}
@@
   in a systematic way by applying architectures to discharge
-  individual system requirements.  Here, we are more interested by the
+  individual system requirements.  Here, we are more interested in the
   properties of the Failure Monitor architecture by itself.  For that
@@
 that \Simon{the only loop starting in the state $\ostate{s1,t1}$ and involving neither $\mathit{reset}$, nor $\mathit{resume}$ or $\mathit{ask}$, is the self-loop $\mathit{fail(b0)}$.
-By further inspecting the synchronisation vector $SV0$, we observe that this self-loop corresponds to the transitions $\mathit{fail(false)}$ and $\mathit{start(false)}$ in the two pLTSs.
+By further inspecting the synchronisation vector $SV0$, we observe that this self-loop corresponds to the transitions $\mathit{fail(false)}$ and $\mathit{start(false)}$ in the two PLTSs.
 Recall that these transitions (carrying the value $\mathit{false}$) are introduced by the encoding.
@@
 Eclipse Equinox, with Java 1.8.
-
-In the basic cases ($EnableState$, $EnableData$) there is no
-benefit, and even an overhead in the case of $EnableData$,
-because of the extra step of checking SAT at the end of the
-algorithm.
-
-But as soon as there are more OTs in the system and not all
-states are reachable, these tests show a significant benefit of the ``smart'' strategy, in
-the considered use-cases, with 50\% of time saving for the $FailureTimer$,
-over to 80\% for the composition, depending
-on the nature of the examples, but increasing significantly
-with their complexity.
 
@@
 
+In the basic cases ($EnableState$, $EnableData$) there is no
+benefit, and even an overhead in the case of $EnableData$,
+because of the extra step of checking SAT at the end of the
+algorithm.
+
+But as soon as there are more OTs in the system and not all
+states are reachable, these tests show a significant benefit of the ``smart'' strategy, in
+the considered use-cases, with 50\% of time saving for the $FailureTimer$,
+over to 80\% for the composition, depending
+on the nature of the examples, but increasing significantly
+with their complexity.
+
 \section{Conclusion and Discussion}
@@
 
-We validate the approach on \Simon{a larger example},%\st{two larger examples}, 
+We validate the approach on \Simon{a larger example}, %\st{two larger examples}, 
 based on a BIP architecture taken from an earlier nanosatellite case
@@
 The question then naturally arises of whether some version of open pNets (\eg extended to accommodate a parameterised number of sub-pNets) can be used to verify certain architectural styles without instantiating them with fixed parameter values.
-Although this problem is know to be undecidable in the general case (see, \eg \cite{KKW+16-foil-concur}), it would be interesting to study the interplay of existing techniques, such as well structured transition systems \cite{WSTSE!}, with open pNet extensions.}
+Although this problem is known to be undecidable in the general case (see, \eg \cite{KKW+16-foil-concur}), it would be interesting to study the interplay of existing techniques, such as well structured transition systems \cite{WSTSE!}, with open pNet extensions.}
 

### 2019-11-20 2017-Xudong-SMT/ActaInformatica.tex
typos

@@
 ensures the termination of our semantic construction algorithm.
-Note that this theorem and its proof were part of previous versions of this work, when Algorithm 1 did not include the fixpoint Refinement computation.
-Proof of termination of the fixpoint itself will be discussed as part of the proof of Theorem \ref{Th:CorrectnessWithAssignments}.
+Note that this theorem and its proof were part of previous versions of this work, when Algorithm 1 did not include the fixed point refinement computation.
+Proof of termination of the fixed point itself will be discussed as part of the proof of Theorem \ref{Th:CorrectnessWithAssignments}.
 

### 2019-12-03 2016-Weak-FH-Bisim/WeakBisim.tex
Nouveaux TODOs, et modifs dessins

@@
 the full system should be equivalent (e.g. through weak bisimulation)
-to the two processes connected simply through a perfect medium.
+to the two processes connected simply through a perfect medium. \TODO{Decrire syntaxe graphique}
 
 Fig.
-\ref{SimpleProt:Impl} show the pNet model of the protocol implementation.
+\ref{SimpleProt:Impl} shows the pNet model of the protocol implementation.
 When the $Medium$ detects an error (modeled by a local $\tau$ action), it sends back a $m\_error$ message to the $Sender$.
-The $Sender$ increments its local error counter $c$, and resends the message (including $c$) to the $Medium$, that will, eventually, transmit $m,c$ to the $Receiver$.
+The $Sender$ increments its local error counter $ec$, and resends the message (including $ec$) to the $Medium$, that will, eventually, transmit $m,ec$ to the $Receiver$.
 
@@
 set of state modifications. This section defines open automata and a bisimulation theory for them.
+\TODO{Add initialisation of state vars}
 
@@
  Open automata (OA) are not composition structures but they are made of transitions that are dependent of the actions of the holes, and they can reason on variables (potentially with only symbolic values).
-Formaly, each state of an OA has set of \emph{state variables}, and all state variable sets are disjoint.
+Formaly, each state of an OA has a set of \emph{state variables}, and all state variable sets are disjoint.
 %\TODO{adopt a uniform notation for open transitions, almost each instance has a 
@@
 
-\TODO{have a look at the end of the sec}
+%\TODO{have a look at the end of the sec}
 
@@
 
-\TODO{Eric: rewrite example with new Protocol}
+\TODO{Eric: rewrite example with new Protocolkeep only OT1, and adapt comments}
 \begin{example}\emph{An open-transition.}
@@
 
-  The \emph{SimpleProtocol} pNet of Fig. \ref{SimpleProt:Spec} has 3 controllers and no holes. One of its possible open-transition (the sender sending $(m)$ to the medium) is:
-
- \smallskip\noindent
- $  OT_2  = \openrule{
-   \emptyset; Pred=[send(SV2\_m)=send(s_1\_m);in(SV2\_m)=in(?m)];  \\ Post=\{m_1\_m:=?m\}
-                      }
-    {\ostate{s_1,m_0,r_0} \OTarrow{\underline{send(SV2\_m)}} \ostate{s_2,m_1,r_0}}
-    $
-
-    That can be simplified to:
-
-    \ERIC{Apres application des substitutions et simplification du predicat:}
-
-     $  OT_2  = \openrule{
-      \emptyset; Pred=\True;  \\ Post=\{m_1\_m:=s_1\_m\}
-                      }
-    {\ostate{s_1,m_0,r_0} \OTarrow{\underline{send(s_1\_m)}} \ostate{s_2,m_1,r_0}}
-    $
-
-    \smallskip
-    Note that the global states shows how the sender and the
-    first medium have evolved during this transition, the sender
-    moving from $s_1$ to $s_2$, and the first (forward) medium from
-    $m_0$ to $m_1$.
-    The predicate $Pred$ involves the state variables $s_1\_m$ and
-    $s_1\_sb$ of the sender, while the assignment $Post$ sets the
-    state variables of the medium.
+ %%  The \emph{SimpleProtocol} pNet of Fig. \ref{SimpleProt:Spec} has 3 controllers and no holes. One of its possible open-transition (the sender sending $(m)$ to the medium) is:
+
+ %% \smallskip\noindent
+ %% $  OT_2  = \openrule{
+ %%   \emptyset; Pred=[send(SV2\_m)=send(s_1\_m);in(SV2\_m)=in(?m)];  \\ Post=\{m_1\_m:=?m\}
+ %%                      }
+ %%    {\ostate{s_1,m_0,r_0} \OTarrow{\underline{send(SV2\_m)}} \ostate{s_2,m_1,r_0}}
+ %%    $
+
+ %%    That can be simplified to:
+
+ %%    \ERIC{Apres application des substitutions et simplification du predicat:}
+
+ %%     $  OT_2  = \openrule{
+ %%      \emptyset; Pred=\True;  \\ Post=\{m_1\_m:=s_1\_m\}
+ %%                      }
+ %%    {\ostate{s_1,m_0,r_0} \OTarrow{\underline{send(s_1\_m)}} \ostate{s_2,m_1,r_0}}
+ %%    $
+
+ %%    \smallskip
+ %%    Note that the global states shows how the sender and the
+ %%    first medium have evolved during this transition, the sender
+ %%    moving from $s_1$ to $s_2$, and the first (forward) medium from
+ %%    $m_0$ to $m_1$.
+ %%    The predicate $Pred$ involves the state variables $s_1\_m$ and
+ %%    $s_1\_sb$ of the sender, while the assignment $Post$ sets the
+ %%    state variables of the medium.
 
@@
 
-\paragraph{Variable management.}
-The variables in each synchronisation vector are considered local:
-for a given pNet expression, we must have fresh local variables for
-each occurrence of a vector (i.e. each time we instantiate rule
-\TrDeux). Similarly the state variables of each copy of a
-given pLTS in the system, must be distinct, and those created for each
-application of \TrDeux\ have to be fresh and all distinct. 
-This is implemented within the open-automaton generation algorithm,
-using name generation using a global counter as a suffix.
-
 %\subsection{Computing and using open automata}
@@
 
-Given an open-pNet
+We have shown in \cite{henrio:Forte2016} that an open-pNet
 with finite synchronisation sets, finitely many leaves and
 holes, and each pLTS at leaves having a finite number of states and
-(symbolic) transitions, has a finite automaton (see \cite{henrio:Forte2016}). The algorithm for building such an automaton can be found in~\cite{QBMZ-AVOCS18}.
+(symbolic) transitions, has a finite automaton. The algorithm for building such an automaton can be found in~\cite{QBMZ-AVOCS18}.
 
@@
 
-\TODO{Eric: full (???) result of the tool execution on the running example on the Simple Prot Spec: Done, on the Counetr version !}
-
-\TODO{:  and maybe one example on the Impl. OTs presented in latex readable form??}
+%\TODO{Eric: full (???) result of the tool execution on the running example on the Simple Prot Spec: Done, on the Counetr version !}
+
+\paragraph{Example} Figure \ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the Specification pNet in Figure \ref{SimpleProt:Spec}.
+
+%\TODO{:  and maybe one example on the Impl. OTs presented in latex readable form??}
+\TODO{Comment on Fig 3...}
 
@@
 \end{figure}
+
+Figure \ref{SimpleProtCounter:ImplOA} shows the full open automaton of the implementation $SimpleSystem$.
+Here, in the open automaton drawing, we use a user-friendly notation for the OTs, in the form ``$\{<actions of holes\} [<guard>] <action> \{assignments\}$''.
+\TODO{comment on difference from Exemple 1 page 15; and predicate simplification...}
+\begin{figure}[h]
+  \centerline{\includegraphics[width=10cm]{ATG/SPImplOpen}}
+  \caption{Open Automaton of the Simple Protocol Implementation}  \label{SimpleProtCounter:ImplOA}
+\end{figure}
+
+%% We show here the first open transition, written here in the form of the tool full output.
+
+%% $  OT_1  = \openrule{
+%%   (P\mapsto p\_send(m:sva\_SV6:1:1)) \\
+%%   [( msg =m: sva\_SV6 :1:1) \wedge (( in( msg ))=( in(m: sva_SV6 :1:1)))]\\
+%%   \{ s1\_msg := msg , s1\_c := 0\}
+%%                       }
+%% {\ostate{s_0,m_0,r_0} \OTarrow{\underline{in(m:sva\_SV6:1:1)}} \ostate{s_1,m_0,r_0}}
+%% $
+    \TODO{Comment...}
 
@@
 Two pNets are FH-bisimilar if there exist a relation between their associated 
-automata that is an FH-bisimulation and their initial states are in the relation, i.e. 
-the predicate associated to the relation between the initial states is \True.
+automata that is an FH-bisimulation and their initial states are in the relation (with some initial predicate).
+\TODO{check}
 \end{definition}
-\TODO{Predicate=True me pose un probleme... typiquement, on a besoin d'une ``condition initiale'', pour avoir des pNets data-oriented equivalents a leur version state-oriebted}
+%\TODO{Predicate=True me pose un probleme...
+typiquement, on a besoin d'une ``condition initiale'', pour avoir des pNets data-oriented equivalents a leur version state-oriebted => remove the constraint}
 
@@
 \end{theorem}
-This theorem is quite powerful somehow states that the theory of open pNets is convenient to study properties of process composition.
+This theorem is quite powerful.
+It somehow implies that the theory of open pNets is convenient to study properties of process composition.
 Open pNets can indeed be used to study process operators and process algebras, as shown in~\cite{henrio:Forte2016}, or to study interaction protocols~\cite{BHHM:FACS11}.
@@
 
-\TODO{Eric: try to draw (ATG) the weak transitino versions of the Simple Protocol, both Spec (easy) and Impl (check readability?)}
+\begin{example}
+  Figure \ref{SimpleProtCounter:SpecOA-partial} show a partial view of the weak automaton of the simple protocol implementation.
+
+\TODO{Explain the partial OA, and comment on building of WOT1}
+\end{example}
+
+\begin{figure}[t]
+   \centerline{\includegraphics[width=12cm]{ATG/SPImplWeakOpen}}
+  \caption{Weak Open Automaton, partial}
+   \label{SimpleProtCounter:SpecOA-partial}
+\end{figure}
 
 \subsection{Composition properties: composition of weak open transitions}
-We now have two different semantics for open pNets: a stronf semantics, defined  as an open automaton, and as a weak semantics, defined as a weak open automaton.
+We now have two different semantics for open pNets: a strong semantics, defined  as an open automaton, and as a weak semantics, defined as a weak open automaton.
 Like the open automaton, the weak open automaton features valuable composition properties.
@@
 \begin{definition}[Notation: Semantics of pNets as a weak open automaton]
-Let $A$ be the open automaton expressing the semantics of an open \pNet: $\pNet$; let $<J,\mathcal{S},s_0,  \WT>$ be the weak open automata derived from $A$.
+Let $A$ be the open automaton expressing the semantics of an open pNet $\pNet$; let $<J,\mathcal{S},s_0,  \WT>$ be the weak open automata derived from $A$.
 For any $\WOT\in\WT$, we denote $\pNet \models \WOT$, this defines the semantics of the pNet $\pNet$ as a weak open automaton.
+\TODO{strange sentence}
 \end{definition}
@@
 \TODO{Je ne pense pas que nous ayons un algo de bisim weak operationnel pour la publi, mais ca n'est pas completement impossible nonp[l;us...
-Au pire, argumenter intuitivement sur papier, en donnat les classes d'equivalence et les predicats.
-    Noter que la version de base est trop simple... Pour avoir des predicats moins triviaux, on peut ajouter un compteur qui compte le nb d'erreurs, et le transmet a la fin}
+Au pire, argumenter intuitivement sur papier, en donnat les classes d'equivalence et les predicats.}
 
@@
 
+\TODO{Eric: rewrite completely}
 \noindent
@@
 
+\TODO{keep ?}
+\paragraph{Variable management.}
+The variables in each synchronisation vector are considered local:
+for a given pNet expression, we must have fresh local variables for
+each occurrence of a vector (i.e. each time we instantiate rule
+\TrDeux). Similarly the state variables of each copy of a
+given pLTS in the system, must be distinct, and those created for each
+application of \TrDeux\ have to be fresh and all distinct. 
+This is implemented within the open-automaton generation algorithm,
+using name generation using a global counter as a suffix.
+
 \begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
@@
   \centerline{\includegraphics[width=10cm]{ATG/SPImplOpen}}
-  \caption{Open Automaton of the Simple Protocol Implementation}  \label{SimpleProtCounter:ImplOA}
+  \caption{Open Automaton of the Simple Protocol Implementation}  \label{Annex:SimpleProtCounter:ImplOA}
 \end{figure}
@@
 \end{figure}
+
+In Figure \ref{Annex:SimpleProtCounter:ImplWOA}, we have added some of the weak transitions generated by the saturation, namely:
+- a tau-loop on each state
+- a transition from <s0\_a0\_r0> to <s2\_a1\_r0>, resulting from the sequence OT\-1;OT\-6 followed by any number of the loop (OT\_9;ot\_12;OT\_6).
+
+Many weak should be added, e.g. Tau loops on states <s2\_a1\_r0>, <s2\_a2\_r0>, 
+<s2\_a0\_r0>, encoding the loop.
 

### 2019-12-04 2016-Weak-FH-Bisim/WeakBisim.tex
added WOT construction

@@
 
+%% \begin{figure}[ht]
+%%    \centerline{\includegraphics[width=12cm]{ATG/WOT1}}
+%%   \caption{Construction of the Weak Open transition WOT1}
+%%    \label{WOT1}
+%% \end{figure}
+
+\begin{figure}[ht]
+   \centerline{\includegraphics[width=11cm]{ATG/WOT2}}
+  \caption{Construction of WOT2}
+   \label{WOT2}
+\end{figure}
+
 \begin{example}
-  Figure \ref{SimpleProtCounter:SpecOA-partial} show a partial view of the weak automaton of the simple protocol implementation.
-
-\TODO{Explain the partial OA, and comment on building of WOT1}
+  Figures \ref{WOT2} shows the construction of one of the weak transitions of the Specification OA.
+We show on the top one possible sequence corresponding to a weak transition, on the bottom left the concerned subset of the original OA, and on the right the generated weak transition.
+\end{example}
+
+%  In the case of WOT1, we start with a tau loop, then change state with an action of hole $P$ to state 1, initializing the $ec$ counter.
+On state 1, we have two tau loops, on of them increasing the $ec$ counter.
+The resulting weak transition is represented here as a regular expression including assignemnts, rather than the substitutions of the formal definition.
+It can the be abbreviated as: $P\mapsto \texttt{p-send}\ \{(ec:=ec+1)^*$.
+
+  WOT2 here is the transition delivering the result of the algorithm to hole $Q$.
+Remark that it includes a loop increasing the counter occurs before the action of $Q$, and this action is using the value of the counter.
+Let us go into the details, using rules WT1/2/3.
+For simplification we ignore the pure $\tau$-loops before and after the central \texttt{q-recv(ec)} action, they have no effect on the construction.
+First consider application of Rule WT3 on the first 3 transitions.
+Hole actions and predicates are empty, we just concentrate on the Post operations.
+Rule WT2 transforms each 3 OTs into WOTs.
+In the drawing we use \texttt{ec++} to abbreviate the Post: $\subst{ec\gets ec+1}$.
+Then WT3 produces the weak OT:
+  $\openrule
+         {\set{\tau}, True,
+			\subst{\texttt{ec++}\shortotimes\texttt{ec++}\shortotimes\emptyset} }
+         {s \OTWeakarrow {\tau\subst{\texttt{ec++}}} s'}$
+         that you can rewrite as:      
+  $\openrule
+         {\emptyset, True,
+			\subst{ec\gets ec+2} }
+         {s \OTWeakarrow \tau s'}$
+
+         Now you can iterate this construction an arbitrary number of times, getting for any natural number $n$ the weak transition:
+  $\openrule
+         {\emptyset, True,
+			\subst{ec\gets ec+n} }
+         {s \OTWeakarrow \tau s'}$
+
+         For any of these, apply again WT3, using the central \texttt{q-recv(ec)} transition as $\alpha$, and you get:
+      $\openrule
+         {\gamma=\{\texttt{q-revc(ec)}\subst{ec\gets ec+n}\}, True,
+			\subst{ec\gets ec+n} }
+         {s \OTWeakarrow {\texttt{q-recv(ec)}\subst{ec\gets ec+n}} s'}$
+
+  \begin{example}
+    Figure \ref{SimpleProtCounter:WeakSpecOA} shows the weak automaton of the simple protocol specification.
+    \TODO{comment...}
+\end{example}
+
+\begin{figure}[ht]
+   \centerline{\includegraphics[width=10cm]{ATG/SPSpecWeakOpen}}
+  \caption{Weak Open Automaton of the Specification}
+   \label{SimpleProtCounter:WeakSpecOA}
+\end{figure}
+
+  \begin{example}
+  Figure \ref{SimpleProtCounter:SpecOA-partial} shows a partial view of the weak automaton of the simple protocol implementation.
+
+\TODO{Explain the partial OA}
 \end{example}
@@
    \centerline{\includegraphics[width=12cm]{ATG/SPImplWeakOpen}}
-  \caption{Weak Open Automaton, partial}
+  \caption{Weak Open Automaton of the implementation, partial}
    \label{SimpleProtCounter:SpecOA-partial}

### 2019-12-05 2016-Weak-FH-Bisim/WeakBisim.tex
updated the listing in last appendix

@@
 state a0
-transition in(msg) -> a1 {a1_msg:=msg}
+transition in(msg) -> a1 {a1_msg:=msg, m1_ec:=0}
 
 state a1
-vars a1_msg:Data {m1_c:=0}:Int
-
-transition out(a1_msg, m1_c) -> a0
-transition synchro($tau)  -> a1 {m1_c:=m1_c+1}
+vars a1_msg:Data m1_ec:Int
+transition out(a1_msg, m1_ec) -> a0
+transition synchro($tau)  -> a1 {m1_ec:=m1_ec+1}
 
@@
 subnets P,M1,Q
-vars p_a,q_a:Action m:Data c:Int
-
-vector SV0 <p_send(m), in(m),_>->p_send(m)
+vars p_a,q_a:Action m:Data ec:Int
+
+vector SV0 <p_send(m), in(m),_>->synchro(in(m))
 vector SV1 <p_a,_,_>->p_a [p_a != p_send(m)]
-vector SV2 <_, out(m,c), q_recv(m)>->q_recv(m,c)
+vector SV2 <_, out(m,ec), q_recv(m)>->synchro(out(m,ec))
 vector SV3 <_,_,q_a>->q_a [q_a != q_recv(m)]
@@
 \begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
-SimpleProtImpl:
+SimpleProtImpl2:
 import "Data_Alg.algp"
-
 root SimpleProtImpl2
@@
 const tau,p_send,q_recv,m_recv,m_send,m_error: Action
-const s_send,s_ack,s_error,r_recv,r_ack: Action
+const s_recv,s_send,s_ack,s_error,r_recv,r_ack,r_send: Action
 
@@
 state s0
-transition in(msg) -> s1 {s1_msg:=msg, s1_c:=0}
+transition s_recv(msg) -> s1 {s1_msg:=msg, s1_c:=0}
 
@@
 vars s1_msg:Data s1_c:Int
-transition s_send(s1_msg, s1_c) -> s2
+transition s_send(s1_msg, s1_c) -> s2 {s2_c:=s1_c}
 
@@
 vars r1_msg:Data r1_c:Int
-transition out(r1_msg, r1_c) -> r2
+transition r_send(r1_msg, r1_c) -> r2
 
@@
   vars m:Data c:Int
-vector SV0 <in(m), _, _>->in(m)
+vector SV0 <s_recv(m), _, _>->in(m)
 vector SV1 <s_send(m,c), m_recv(m,c), _>->synchro($tau)
-vector SV2 <_, m_send(m), r_recv(m)>->synchro($tau)
+vector SV2 <_, m_send(m,c), r_recv(m,c)>->synchro($tau)
 vector SV3 <$s_ack, _, $r_ack>->synchro($tau)
 vector SV4 <$s_error, $m_error, _>->synchro($tau)
-vector SV5 <_, _, out(m,c)>->out(m,c)
+vector SV5 <_, _, r_send(m,c)>->out(m,c)
 
@@
   vars p_a,q_a:Action  m:Data c:Int
-vector SV0 <p_send(m), in(m),_>->in(m)
+vector SV0 <p_send(m), in(m),_>->synchro(in(m))
 vector SV1 <p_a,_,_>->p_a [p_a != p_send(m)]
-vector SV2 <_, out(m,c), q_recv(m,c)>->out(m,c)
+vector SV2 <_, out(m,c), q_recv(m,c)>->synchro(out(m,c))
 vector SV3 <_,_,q_a>->q_a [q_a != q_recv(m,c)]
@@
 
-Finaly, we list here, in raw format, the 12 OTs computed by the tool
-\TODO{BUG! We should have 19 OTs...}:
+Finaly, we list here, in raw format, the 19 OTs computed by the tool for the SimpleProtImpl pNet:
 
@@
 {P|->p_send(m:sva_SV6:1:1)},
-	[(msg=m:sva_SV6:1:1)/\((in(msg))=(in(m:sva_SV6:1:1)))],
-	{s1_msg := msg, s1_c := 0}
+[(msg=m:sva_SV0:12:1)/\((s_recv(msg))=(s_recv(m:sva_SV0:12:1)))],   {s1_msg := msg, s1_c := 0}
 	OT:1 ------------------------------------------------------------
-	<s0_a0_r0>-----in(m:sva_SV6:1:1)----><s1_a0_r0>
+		<s0_a0_r0>-----_in(m:sva_SV6:1:1)_----><s1_a0_r0>
 
@@
 {P|->p_a:sva_SV7:1:2},
-	[(forall:m:sva_SV7:1:2.
-          (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
+[(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
 	OT:2 ------------------------------------------------------------
@@
 {Q|->q_a:sva_SV9:1:4},
-	[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4.
-          (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
+[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
 	OT:3 ------------------------------------------------------------
@@
 {Q|->q_a:sva_SV9:1:4},
-	[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4.
-          (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
+[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
 	OT:5 ------------------------------------------------------------
@@
   /\((m_recv(msg, c))=(m_recv(m:sva_SV1:114:2, c:sva_SV1:114:2)))],
-	{a1_msg := msg, a1_c := c}
+{s2_c := s1_c, a1_msg := msg, a1_c := c}
 	OT:6 ------------------------------------------------------------
@@
 {Q|->q_a:sva_SV9:1:4},
-	[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4.
-          (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
+[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
 	OT:8 ------------------------------------------------------------
@@
 INFO  SimpleProtImpl2 - 
+{},   [(a1_msg=m:sva_SV2:114:3)/\(a1_c=c:sva_SV2:114:3)
+  /\((m_send(a1_msg, a1_c))=(m_send(m:sva_SV2:114:3, c:sva_SV2:114:3)))
+  /\(msg=m:sva_SV2:114:3)/\(c=c:sva_SV2:114:3)
+  /\((r_recv(msg, c))=(r_recv(m:sva_SV2:114:3, c:sva_SV2:114:3)))],
+{r1_msg := msg, r1_c := c}
+	OT:9 ------------------------------------------------------------
+		<s2_a1_r0>-----_tau_----><s2_a0_r1>
+
+INFO  SimpleProtImpl2 - 
 		{},   [],   {}
-OT:9 ------------------------
+	OT:10 ------------------------
 		<s2_a1_r0>-----_tau_----><s2_a2_r0>
@@
 [(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
-OT:10 ------------------------------------------------------------
-	<s2_a2_r0>-----p_a:sva_SV7:1:2----><s2_a2_r0>
+	OT:11 ------------------------------------------------------------
+		<s2_a0_r1>-----p_a:sva_SV7:1:2----><s2_a0_r1>
+
+INFO  SimpleProtImpl2 - 
+{Q|->q_recv(m:sva_SV8:1:3, c:sva_SV8:1:3)},
+[(r1_msg=m:sva_SV5:18:6)/\(r1_c=c:sva_SV5:18:6)
+  /\((r_send(r1_msg, r1_c))=(r_send(m:sva_SV5:18:6, c:sva_SV5:18:6)))],   {}
+	OT:12 ------------------------------------------------------------
+		<s2_a0_r1>-----_out(m:sva_SV8:1:3, c:sva_SV8:1:3)_----><s2_a0_r2>
 
@@
 {Q|->q_a:sva_SV9:1:4},
-	[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4.
-          (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
-OT:11 ------------------------------------------------------------
+[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
+	OT:13 ------------------------------------------------------------
+		<s2_a0_r1>-----q_a:sva_SV9:1:4----><s2_a0_r1>
+
+INFO  SimpleProtImpl2 - 
+{P|->p_a:sva_SV7:1:2},
+[(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
+	OT:14 ------------------------------------------------------------
+		<s2_a2_r0>-----p_a:sva_SV7:1:2----><s2_a2_r0>
+
+INFO  SimpleProtImpl2 - 
+{Q|->q_a:sva_SV9:1:4},
+[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
+	OT:15 ------------------------------------------------------------
 		<s2_a2_r0>-----q_a:sva_SV9:1:4----><s2_a2_r0>
@@
 		{},   [],   {s1_c := s2_c+1}
-OT:12 --------------------------------------
+	OT:16 --------------------------------------
 		<s2_a2_r0>-----_tau_----><s1_a0_r0>
 
-INFO   SimpleProtImpl2 - State variables:
-
+INFO  SimpleProtImpl2 - 
+{P|->p_a:sva_SV7:1:2},
+[(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
+	OT:17 ------------------------------------------------------------
+		<s2_a0_r2>-----p_a:sva_SV7:1:2----><s2_a0_r2>
+
+INFO  SimpleProtImpl2 - 
+{Q|->q_a:sva_SV9:1:4},
+[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
+	OT:18 ------------------------------------------------------------
+		<s2_a0_r2>-----q_a:sva_SV9:1:4----><s2_a0_r2>
+
+INFO  SimpleProtImpl2 - 
+		{},   [],   {}
+	OT:19 ------------------------
+		<s2_a0_r2>-----_tau_----><s0_a0_r0>
+
+DEBUG SimpleProtImpl2 - 
 Global State: <s0_a0_r0>
@@
 
+DEBUG SimpleProtImpl2 - 
 Global State: <s1_a0_r0>
 ===================
-pLTS States: <s1 vars: { s1_c <-{0, s2_c+1, } s1_msg <-{msg, }}> <a0 vars: {}> <r0 vars: {}>
-
+pLTS States: <s1 vars: { s1_msg <-{msg, } s1_c <-{0, s2_c+1, }}> <a0 vars: {}> <r0 vars: {}>
+
+DEBUG SimpleProtImpl2 - 
 Global State: <s2_a1_r0>
 ===================
-pLTS States: <s2 vars: {}> <a1 vars: { a1_msg <-{msg, } a1_c <-{c, }}> <r0 vars: {}>
-
+pLTS States: <s2 vars: { s2_c <-{s1_c, }}> <a1 vars: { a1_msg <-{msg, } a1_c <-{c, }}> <r0 vars: {}>
+
+DEBUG SimpleProtImpl2 - 
+Global State: <s2_a0_r1>
+===================
+pLTS States: <s2 vars: { s2_c <-{s1_c, }}> <a0 vars: {}> <r1 vars: { r1_c <-{c, } r1_msg <-{msg, }}>
+
+DEBUG SimpleProtImpl2 - 
 Global State: <s2_a2_r0>
 ===================
-pLTS States: <s2 vars: {}> <a2 vars: {}> <r0 vars: {}>
-
-INFO  SimpleProtImpl2 - Total: 12 SATISFIABLE OTs
-INFO  SimpleProtImpl2 -        122 UNSATISFIABLE OTs
-INFO  SimpleProtImpl2 - Total Time: 657 ms
+pLTS States: <s2 vars: { s2_c <-{s1_c, }}> <a2 vars: {}> <r0 vars: {}>
+
+DEBUG SimpleProtImpl2 - 
+Global State: <s2_a0_r2>
+===================
+pLTS States: <s2 vars: { s2_c <-{s1_c, }}> <a0 vars: {}> <r2 vars: {}>
+
+INFO  SimpleProtImpl2 - Total: 19 SATISFIABLE OTs
+INFO  SimpleProtImpl2 -        185 UNSATISFIABLE OTs
+INFO  SimpleProtImpl2 - Total Time: 1105 ms
 

### 2019-12-05 2016-Weak-FH-Bisim/WeakBisim.tex
add comment Fig.1

@@
 the full system should be equivalent (e.g. through weak bisimulation)
-to the two processes connected simply through a perfect medium. \TODO{Decrire syntaxe graphique}
+to the two processes connected simply through a perfect medium. \TODO{ 
+The pNet has a tree-like structure.  The root node of the tree {\it SimpleSystemSpec} is the top level of the pNet structure. It acts
+as the parallel operator.
+It consists of tree nodes: two Holes $P$ and $Q$ and one subnet, noted {\it PrefectMedium}.
+Nodes of the tree are synchronized using four synchronization vectors, that  express the possible synchronization between the parameterized actions of a subset of the nodes.
+For instance, in the vector "$< p\_send(m),in(m),\_> \rightarrow \underline{in(m)}$ both $P$ and {\it PrefectMedium} nodes are involved in the synchronization.
+In particular, this means the synchronization between these processes occurs when  process $P$  performs $p\_send(m)$  action sending a message, and  the medium accepts the message through $in(m)$ action  at the same time.
+And the result that will be returned at upper level is the internal action  $\underline{in(m)}$.
+}
 

### 2019-12-06 2016-Weak-FH-Bisim/WeakBisim.tex
2 more TODOs done.

@@
 the full system should be equivalent (e.g. through weak bisimulation)
-to the two processes connected simply through a perfect medium. \TODO{ 
+to the two processes connected simply through a perfect medium. \RAB{ 
 The pNet has a tree-like structure.  The root node of the tree {\it SimpleSystemSpec} is the top level of the pNet structure. It acts
@@
 set of state modifications. This section defines open automata and a bisimulation theory for them.
-\TODO{Add initialisation of state vars}
+\TODO{Add initialisation of state vars: done in Defn of OA}
 
@@
 		  among $\mathcal{S}$,
+                  \item[$\bullet$] for each state $s$, $vars(s)=\{v_s\}$ is a set of state variables, and each $v_s$ may have an initial value $init(v_s)$.
 		\item[$\bullet$] $\mathcal{T}$ is a set of open transitions and for each
@@
 
-\TODO{Eric: rewrite example with new Protocolkeep only OT1, and adapt comments}
+%\TODO{Eric: rewrite example with new Protocolkeep only OT1, and adapt comments}
 \begin{example}\emph{An open-transition.}
@@
 At the upper level, the $SimpleSystem$ pNet has 2 holes and $SimpleProtocol$ as
-a subnet. One of its possible open transitions (synchronizing the hole $P$
+a subnet, itself containing 3 pLTSs. One of its possible open transitions
+(synchronizing the hole $P$
 with the $Sender$ within the \emph{SimpleProtocol}) is:
@@
     \smallskip
-    The global states here have the same structure than
-    in $OT_2$, as the holes have no states. The assignment
+    The global states here are triples, build as the product of states of the 3 pLTS (remember the Holes have no state). The assignment
     $Post$ uses a variable from the action of hole $P$ to set the
     value of the sender state variable $s1\_m$.
+    \TODO{need more comments ?}
 
@@
 
-And here is a  drawing of this open automaton, slightly simplified for readability:
-
-\begin{figure}[h]
-  \centerline{\includegraphics[width=10cm]{ATG/SPImplOpen}}
-  \caption{Open Automaton of the Simple Protocol Implementation}  \label{Annex:SimpleProtCounter:ImplOA}
-\end{figure}
-
-And a partially saturated Automaton:
-
-\begin{figure}[h]
-  \centerline{\includegraphics[width=13cm]{ATG/SPImplWeakOpen}}
-  \caption{Weak Open Automaton, partial}  \label{SimpleProtCounter:ImplWOA}
-\end{figure}
-
-In Figure \ref{Annex:SimpleProtCounter:ImplWOA}, we have added some of the weak transitions generated by the saturation, namely:
-- a tau-loop on each state
-- a transition from <s0\_a0\_r0> to <s2\_a1\_r0>, resulting from the sequence OT\-1;OT\-6 followed by any number of the loop (OT\_9;ot\_12;OT\_6).
+%% And here is a  drawing of this open automaton, slightly simplified for readability:
+
+%% \begin{figure}[h]
+%%   \centerline{\includegraphics[width=10cm]{ATG/SPImplOpen}}
+%%   \caption{Open Automaton of the Simple Protocol Implementation}  \label{Annex:SimpleProtCounter:ImplOA}
+%% \end{figure}
+
+%% And a partially saturated Automaton:
+
+%% \begin{figure}[h]
+%%   \centerline{\includegraphics[width=13cm]{ATG/SPImplWeakOpen}}
+%%   \caption{Weak Open Automaton, partial}  \label{SimpleProtCounter:ImplWOA}
+%% \end{figure}
+
+%% In Figure \ref{Annex:SimpleProtCounter:ImplWOA}, we have added some of the weak transitions generated by the saturation, namely:
+%% - a tau-loop on each state
+%% - a transition from <s0\_a0\_r0> to <s2\_a1\_r0>, resulting from the sequence OT\-1;OT\-6 followed by any number of the loop (OT\_9;ot\_12;OT\_6).
 

### 2019-12-09 2016-Weak-FH-Bisim/WeakBisim.tex
nom des etats dans Fig 4; correction dernier listing.

@@
 
-Finaly, we list here, in raw format, the 19 OTs computed by the tool for the SimpleProtImpl pNet:
+Finaly, we list here in raw format, the 19 OTs computed by the tool for the SimpleProtImpl pNet.
+This view uses variable names very close to the internal representation in the tool, allowing for tracability of generated fresh variables. For example:
+\begin{itemize}
+\item m:SV6:1:1 refers to a variable named ``m'' in the synchronisation vector ``SV6''; the last 2 numbers allows to distinguish different clones.
+\item the other variable names reflect our naming policy: state variables are prefixed by the name of the state, holes actions by the name of the hole.
+\end{itemize}
 
 \begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
+
+{P|->p_send(m:SV6:1:1)},
+[(msg=m:SV0:12:1)/\((s_recv(msg))=(s_recv(m:SV0:12:1)))], {s1_msg := msg, s1_c := 0}
+	OT:1 ------------------------------------------------------------
+		<s0_a0_r0>-----_in(m:SV6:1:1)_----><s1_a0_r0>
+
+{P|->p_a:SV7:1:2},
+[(forall:m:SV7:1:2. (p_a:SV7:1:2!=(p_send(m:SV7:1:2)))], {}
+	OT:2 ------------------------------------------------------------
+		<s0_a0_r0>-----p_a:SV7:1:2----><s0_a0_r0>
+
+{Q|->q_a:SV9:1:4},
+[(forall:m:SV9:1:4,c:SV9:1:4. (q_a:SV9:1:4!=(q_recv(m:SV9:1:4, c:SV9:1:4)))],   {}
+	OT:3 ------------------------------------------------------------
+		<s0_a0_r0>-----q_a:SV9:1:4----><s0_a0_r0>
+
 INFO  SimpleProtImpl2 - 
-{P|->p_send(m:sva_SV6:1:1)},
-[(msg=m:sva_SV0:12:1)/\((s_recv(msg))=(s_recv(m:sva_SV0:12:1)))],   {s1_msg := msg, s1_c := 0}
-	OT:1 ------------------------------------------------------------
-		<s0_a0_r0>-----_in(m:sva_SV6:1:1)_----><s1_a0_r0>
-
-INFO  SimpleProtImpl2 - 
-{P|->p_a:sva_SV7:1:2},
-[(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
-	OT:2 ------------------------------------------------------------
-		<s0_a0_r0>-----p_a:sva_SV7:1:2----><s0_a0_r0>
-
-INFO  SimpleProtImpl2 - 
-{Q|->q_a:sva_SV9:1:4},
-[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
-	OT:3 ------------------------------------------------------------
-		<s0_a0_r0>-----q_a:sva_SV9:1:4----><s0_a0_r0>
-
-INFO  SimpleProtImpl2 - 
-{P|->p_a:sva_SV7:1:2},
-[(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
+{P|->p_a:SV7:1:2},
+[(forall:m:SV7:1:2. (p_a:SV7:1:2!=(p_send(m:SV7:1:2)))],   {}
 	OT:4 ------------------------------------------------------------
-		<s1_a0_r0>-----p_a:sva_SV7:1:2----><s1_a0_r0>
-
-INFO  SimpleProtImpl2 - 
-{Q|->q_a:sva_SV9:1:4},
-[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
+		<s1_a0_r0>-----p_a:SV7:1:2----><s1_a0_r0>
+
+{Q|->q_a:SV9:1:4},
+[(forall:m:SV9:1:4,c:SV9:1:4. (q_a:SV9:1:4!=(q_recv(m:SV9:1:4, c:SV9:1:4)))],   {}
 	OT:5 ------------------------------------------------------------
-		<s1_a0_r0>-----q_a:sva_SV9:1:4----><s1_a0_r0>
-
-INFO  SimpleProtImpl2 - 
-{},   [(s1_msg=m:sva_SV1:114:2)/\(s1_c=c:sva_SV1:114:2)
-  /\((s_send(s1_msg, s1_c))=(s_send(m:sva_SV1:114:2, c:sva_SV1:114:2)))
-  /\(msg=m:sva_SV1:114:2)/\(c=c:sva_SV1:114:2)
-  /\((m_recv(msg, c))=(m_recv(m:sva_SV1:114:2, c:sva_SV1:114:2)))],
+		<s1_a0_r0>-----q_a:SV9:1:4----><s1_a0_r0>
+
+{},   [(s1_msg=m:SV1:114:2)/\(s1_c=c:SV1:114:2)
+  /\((s_send(s1_msg, s1_c))=(s_send(m:SV1:114:2, c:SV1:114:2)))
+  /\(msg=m:SV1:114:2)/\(c=c:SV1:114:2)
+  /\((m_recv(msg, c))=(m_recv(m:SV1:114:2, c:SV1:114:2)))],
 {s2_c := s1_c, a1_msg := msg, a1_c := c}
@@
 
-INFO  SimpleProtImpl2 - 
-{P|->p_a:sva_SV7:1:2},
-[(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
+{P|->p_a:SV7:1:2},
+[(forall:m:SV7:1:2. (p_a:SV7:1:2!=(p_send(m:SV7:1:2)))],   {}
 	OT:7 ------------------------------------------------------------
-		<s2_a1_r0>-----p_a:sva_SV7:1:2----><s2_a1_r0>
-
-INFO  SimpleProtImpl2 - 
-{Q|->q_a:sva_SV9:1:4},
-[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
+		<s2_a1_r0>-----p_a:SV7:1:2----><s2_a1_r0>
+
+{Q|->q_a:SV9:1:4},
+[(forall:m:SV9:1:4,c:SV9:1:4. (q_a:SV9:1:4!=(q_recv(m:SV9:1:4, c:SV9:1:4)))],   {}
 	OT:8 ------------------------------------------------------------
-		<s2_a1_r0>-----q_a:sva_SV9:1:4----><s2_a1_r0>
-
-INFO  SimpleProtImpl2 - 
-{},   [(a1_msg=m:sva_SV2:114:3)/\(a1_c=c:sva_SV2:114:3)
-  /\((m_send(a1_msg, a1_c))=(m_send(m:sva_SV2:114:3, c:sva_SV2:114:3)))
-  /\(msg=m:sva_SV2:114:3)/\(c=c:sva_SV2:114:3)
-  /\((r_recv(msg, c))=(r_recv(m:sva_SV2:114:3, c:sva_SV2:114:3)))],
+		<s2_a1_r0>-----q_a:SV9:1:4----><s2_a1_r0>
+
+{},   [(a1_msg=m:SV2:114:3)/\(a1_c=c:SV2:114:3)
+  /\((m_send(a1_msg, a1_c))=(m_send(m:SV2:114:3, c:SV2:114:3)))
+  /\(msg=m:SV2:114:3)/\(c=c:SV2:114:3)
+  /\((r_recv(msg, c))=(r_recv(m:SV2:114:3, c:SV2:114:3)))],
 {r1_msg := msg, r1_c := c}
@@
 
-INFO  SimpleProtImpl2 - 
 		{},   [],   {}
@@
 
-INFO  SimpleProtImpl2 - 
-{P|->p_a:sva_SV7:1:2},
-[(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
+{P|->p_a:SV7:1:2},
+[(forall:m:SV7:1:2. (p_a:SV7:1:2!=(p_send(m:SV7:1:2)))],   {}
 	OT:11 ------------------------------------------------------------
-		<s2_a0_r1>-----p_a:sva_SV7:1:2----><s2_a0_r1>
-
-INFO  SimpleProtImpl2 - 
-{Q|->q_recv(m:sva_SV8:1:3, c:sva_SV8:1:3)},
-[(r1_msg=m:sva_SV5:18:6)/\(r1_c=c:sva_SV5:18:6)
-  /\((r_send(r1_msg, r1_c))=(r_send(m:sva_SV5:18:6, c:sva_SV5:18:6)))],   {}
+		<s2_a0_r1>-----p_a:SV7:1:2----><s2_a0_r1>
+
+{Q|->q_recv(m:SV8:1:3, c:SV8:1:3)},
+[(r1_msg=m:SV5:18:6)/\(r1_c=c:SV5:18:6)
+  /\((r_send(r1_msg, r1_c))=(r_send(m:SV5:18:6, c:SV5:18:6)))],   {}
 	OT:12 ------------------------------------------------------------
-		<s2_a0_r1>-----_out(m:sva_SV8:1:3, c:sva_SV8:1:3)_----><s2_a0_r2>
-
-INFO  SimpleProtImpl2 - 
-{Q|->q_a:sva_SV9:1:4},
-[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
+		<s2_a0_r1>-----_out(m:SV8:1:3, c:SV8:1:3)_----><s2_a0_r2>
+
+{Q|->q_a:SV9:1:4},
+[(forall:m:SV9:1:4,c:SV9:1:4. (q_a:SV9:1:4!=(q_recv(m:SV9:1:4, c:SV9:1:4)))],   {}
 	OT:13 ------------------------------------------------------------
-		<s2_a0_r1>-----q_a:sva_SV9:1:4----><s2_a0_r1>
-
-INFO  SimpleProtImpl2 - 
-{P|->p_a:sva_SV7:1:2},
-[(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
+		<s2_a0_r1>-----q_a:SV9:1:4----><s2_a0_r1>
+
+{P|->p_a:SV7:1:2},
+[(forall:m:SV7:1:2. (p_a:SV7:1:2!=(p_send(m:SV7:1:2)))],   {}
 	OT:14 ------------------------------------------------------------
-		<s2_a2_r0>-----p_a:sva_SV7:1:2----><s2_a2_r0>
-
-INFO  SimpleProtImpl2 - 
-{Q|->q_a:sva_SV9:1:4},
-[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
+		<s2_a2_r0>-----p_a:SV7:1:2----><s2_a2_r0>
+
+{Q|->q_a:SV9:1:4},
+[(forall:m:SV9:1:4,c:SV9:1:4. (q_a:SV9:1:4!=(q_recv(m:SV9:1:4, c:SV9:1:4)))],   {}
 	OT:15 ------------------------------------------------------------
-		<s2_a2_r0>-----q_a:sva_SV9:1:4----><s2_a2_r0>
-
-INFO  SimpleProtImpl2 - 
+		<s2_a2_r0>-----q_a:SV9:1:4----><s2_a2_r0>
+
 		{},   [],   {s1_c := s2_c+1}
@@
 
-INFO  SimpleProtImpl2 - 
-{P|->p_a:sva_SV7:1:2},
-[(forall:m:sva_SV7:1:2. (p_a:sva_SV7:1:2!=(p_send(m:sva_SV7:1:2)))],   {}
+{P|->p_a:SV7:1:2},
+[(forall:m:SV7:1:2. (p_a:SV7:1:2!=(p_send(m:SV7:1:2)))],   {}
 	OT:17 ------------------------------------------------------------
-		<s2_a0_r2>-----p_a:sva_SV7:1:2----><s2_a0_r2>
-
-INFO  SimpleProtImpl2 - 
-{Q|->q_a:sva_SV9:1:4},
-[(forall:m:sva_SV9:1:4,c:sva_SV9:1:4. (q_a:sva_SV9:1:4!=(q_recv(m:sva_SV9:1:4, c:sva_SV9:1:4)))],   {}
+		<s2_a0_r2>-----p_a:SV7:1:2----><s2_a0_r2>
+
+{Q|->q_a:SV9:1:4},
+[(forall:m:SV9:1:4,c:SV9:1:4. (q_a:SV9:1:4!=(q_recv(m:SV9:1:4, c:SV9:1:4)))],   {}
 	OT:18 ------------------------------------------------------------
-		<s2_a0_r2>-----q_a:sva_SV9:1:4----><s2_a0_r2>
-
-INFO  SimpleProtImpl2 - 
+		<s2_a0_r2>-----q_a:SV9:1:4----><s2_a0_r2>
+
 		{},   [],   {}
@@
 
-DEBUG SimpleProtImpl2 - 
+Assignements of state variables:
+
 Global State: <s0_a0_r0>
@@
 
-DEBUG SimpleProtImpl2 - 
 Global State: <s1_a0_r0>
 ===================
-pLTS States: <s1 vars: { s1_msg <-{msg, } s1_c <-{0, s2_c+1, }}> <a0 vars: {}> <r0 vars: {}>
-
-DEBUG SimpleProtImpl2 - 
+pLTS States: <s1 vars: { s1_msg <-{msg} s1_c <-{0, s2_c+1}}> <a0 vars: {}> <r0 vars: {}>
+
 Global State: <s2_a1_r0>
 ===================
-pLTS States: <s2 vars: { s2_c <-{s1_c, }}> <a1 vars: { a1_msg <-{msg, } a1_c <-{c, }}> <r0 vars: {}>
-
-DEBUG SimpleProtImpl2 - 
+pLTS States: <s2 vars: { s2_c <-{s1_c}}> <a1 vars: { a1_msg <-{msg} a1_c <-{c}}> <r0 vars: {}>
+
 Global State: <s2_a0_r1>
 ===================
-pLTS States: <s2 vars: { s2_c <-{s1_c, }}> <a0 vars: {}> <r1 vars: { r1_c <-{c, } r1_msg <-{msg, }}>
-
-DEBUG SimpleProtImpl2 - 
+pLTS States: <s2 vars: { s2_c <-{s1_c}}> <a0 vars: {}> <r1 vars: { r1_c <-{c} r1_msg <-{msg}}>
+
 Global State: <s2_a2_r0>
 ===================
-pLTS States: <s2 vars: { s2_c <-{s1_c, }}> <a2 vars: {}> <r0 vars: {}>
-
-DEBUG SimpleProtImpl2 - 
+pLTS States: <s2 vars: { s2_c <-{s1_c}}> <a2 vars: {}> <r0 vars: {}>
+
 Global State: <s2_a0_r2>
 ===================
-pLTS States: <s2 vars: { s2_c <-{s1_c, }}> <a0 vars: {}> <r2 vars: {}>
+pLTS States: <s2 vars: { s2_c <-{s1_c}}> <a0 vars: {}> <r2 vars: {}>
 
@@
 %% - a transition from <s0\_a0\_r0> to <s2\_a1\_r0>, resulting from the sequence OT\-1;OT\-6 followed by any number of the loop (OT\_9;ot\_12;OT\_6).
-
-Many weak should be added, e.g. Tau loops on states <s2\_a1\_r0>, <s2\_a2\_r0>, 
-<s2\_a0\_r0>, encoding the loop.
+%%
+%%Many weak should be added, e.g. Tau loops on states <s2\_a1\_r0>, <s2\_a2\_r0>, 
+%%<s2\_a0\_r0>, encoding the loop.
 

### 2019-12-10 2016-Weak-FH-Bisim/WeakBisim.tex
corrections ce matin

@@
 
-\begin{definition}[Sorts, Holes, Leaves of pNets]\label{def-sortholeleave}
+\begin{definition}[Sorts, Holes, Leaves of pNets]\label{def-sortholeleave}~~
+
   \begin{itemize}
@@
 the full system should be equivalent (e.g. through weak bisimulation)
-to the two processes connected simply through a perfect medium. \RAB{ 
-The pNet has a tree-like structure.  The root node of the tree {\it SimpleSystemSpec} is the top level of the pNet structure. It acts
-as the parallel operator.
+to the two processes connected simply through a perfect medium.  
+The pNet has a tree-like structure.
+The root node of the tree {\it SimpleSystemSpec} is the top level of the pNet structure.
+It acts as the parallel operator.
 It consists of tree nodes: two Holes $P$ and $Q$ and one subnet, noted {\it PrefectMedium}.
 Nodes of the tree are synchronized using four synchronization vectors, that  express the possible synchronization between the parameterized actions of a subset of the nodes.
-For instance, in the vector "$< p\_send(m),in(m),\_> \rightarrow \underline{in(m)}$ both $P$ and {\it PrefectMedium} nodes are involved in the synchronization.
+For instance, in the vector "$< p\_send(m),in(m),\_> \rightarrow \underline{in(m)}$ only $P$ and {\it PrefectMedium} nodes are involved in the synchronization.
 In particular, this means the synchronization between these processes occurs when  process $P$  performs $p\_send(m)$  action sending a message, and  the medium accepts the message through $in(m)$ action  at the same time.
 And the result that will be returned at upper level is the internal action  $\underline{in(m)}$.
-}
 
@@
 set of state modifications. This section defines open automata and a bisimulation theory for them.
-\TODO{Add initialisation of state vars: done in Defn of OA}
 
@@
   \label{OT:ABP}
-At the upper level, the $SimpleSystem$ pNet has 2 holes and $SimpleProtocol$ as
+At the upper level, the $SimpleSystem$ pNet of Figure \ref{SimpleProt:Impl} has 2 holes and $SimpleProtocol$ as
 a subnet, itself containing 3 pLTSs. One of its possible open transitions
@@
  \smallskip\noindent
- $  OT_1  = \openrule{
-      (P\mapsto p\_send(m)); Pred=[m=m']; Post=\{s1\_m:=m\}
-                      }
-    {\ostate{s_0,m_0,r_0} \OTarrow{\underline{in(m')}} \ostate{s_1,m_0,r_0}}
-    $
+ \[  OT_1  = \openrule{
+      \{P\mapsto p\_send(m)\} \qquad [m=m'] \qquad \{s1\_m:=m\}
+                      }
+    {\ostate{s_0,a_0,r_0} \OTarrow{\underline{in(m')}} \ostate{s_1,a_0,r_0}}
+    \]
 

### 2019-12-11 2016-Weak-FH-Bisim/WeakBisim.tex
quelques TODO{commentaires} faits

@@
 
-%Ludo
-%\begin{itemize}
-%\item[x] rewrite Tr2 and open transition with actions
-%\item[x] $v'\to \alpha'$ dans pred sv et enlever l exists
-%\item[x] $\beta$ ou $b$
-%\item[x] propager Tr2 dans l annexe
-%\item[x] add simple equivalence on OT -- fait a minima 
-%\item[x] explain the 2 level logic
-%\end{itemize}
-%=== 18 Avril
-\medskip
-
-Eric
-\begin{itemize}
-\item[X] nettoyage (1/2) -> 5 juil
-\item nettoyage exemple et algo de calcul
-\item example -> fin aout -> qq transitions dans l abp
-%\item re-ecrire transitions page 14 comment les presenter?
-%\item arbre de deduction
-%\item exemple avec actions
-\end{itemize}
-
-\medskip
-
-Rabea
-\begin{itemize}
-\item preuve transitivite -> 20 sept
-\item proofs of new theorems -> oct?
-%\item [x] uniformiser p et P pour les pnets 
-%\item [x] relectures
-\end{itemize}
-=== en parallele
-
 \tableofcontents
@@
 trivial). 
-We use sets of equations of the form $x_i=e_i$, ranged over by $\Post$; $\subst{\Post}$ is the substitution that applies all the substitutions defined by $\Post$ in a parallel manner.
+We use \ERIC{sets of assignments of the form $x_i:=e_i$}, ranged over by $\Post$; $\subst{\Post}$ is the substitution that applies all the substitutions defined by $\Post$ in a parallel manner.
 $\otimes$ is the composition operator on substitutions: $(x_k\gets e_k)^{k\in K}\shortotimes \Post =  (x_k\gets e_k\subst{\Post})^{k\in K}$
@@
         \Pred\ is a predicate over the source variables. \Post\ is a set of 
-	equations that hold \emph{after the open transition}, they are
+	\ERIC{assignments that are effective \emph{after the open transition}}, they are
         represented as a substitution of the form $({x_k\gets e_k})^{k\in K}$ 
@@
 \begin{example}\emph{An open-transition.}
-  \label{OT:ABP}
+  \label{OT:SimpleProt}
 At the upper level, the $SimpleSystem$ pNet of Figure \ref{SimpleProt:Impl} has 2 holes and $SimpleProtocol$ as
@@
  \[  OT_1  = \openrule{
-      \{P\mapsto p\_send(m)\} \qquad [m=m'] \qquad \{s1\_m:=m\}
+      \{P\mapsto p\_send(m)\} \qquad [m=m'] \qquad \{s1\_m\gets m\}
                       }
@@
     The global states here are triples, build as the product of states of the 3 pLTS (remember the Holes have no state). The assignment
-    $Post$ uses a variable from the action of hole $P$ to set the
-    value of the sender state variable $s1\_m$.
-    \TODO{need more comments ?}
+    $Post$ uses the variable $m$ from the action of hole $P$ to set the
+    value of the sender state variable named $s1\_m$.
 
@@
 Figure \ref{SimpleProtCounter:ImplOA} shows the full open automaton of the implementation $SimpleSystem$.
-Here, in the open automaton drawing, we use a user-friendly notation for the OTs, in the form ``$\{<actions of holes\} [<guard>] <action> \{assignments\}$''.
-\TODO{comment on difference from Exemple 1 page 15; and predicate simplification...}
+Here, in the open automaton drawing, we use a user-friendly notation for the OTs, in the form ``$\{actions of holes\} [guard] action \{assigns\}$'', rather than the full OT form with the red-dotted rule.
+Note that the resulting action of the OTs appear here betwen the guard and the set of assignments.
+Note that we have also simplified the form of the variable dependencies in the OTs, again for readability, replacing e.g.
+in OT1 $\{P\mapsto p\_send(m)\} \qquad [m=m']$ and $\alpha= \underline{in(m')}$ by the shorter \texttt{\{P->p\_send(m)\} in(m)}.
+
     \begin{figure}[h]
@@
 %% $
-    \TODO{Comment...}
+    \ERIC{Also we have short labels for states, representing $\ostate{s_0,m_0,r_0}$ by \texttt{000}.
+The resulting behavior is quite simple: In every state, holes $P$ and $Q$ can do any action independent of the protocol (we only have labelled these on state \texttt{000}).
+Then we have a main loop including receiving a message from $P$ and transmitting the same message to $Q$, with some intermediate $\tau$ actions from the internal communications between the protocol processes.
+In most of the transitions, you can observe that data is propagated between the successive state variables (holding the message, and the error counter value).
+On th eright of the figure, you have a loop of $\tau$ transitions showing the handling of errors and corresponding increments of the error counter.}
+    \TODO{j'ai comment\'e Fig 3, vous pouvez relire ?}
 
@@
   WOT2 here is the transition delivering the result of the algorithm to hole $Q$.
-Remark that it includes a loop increasing the counter occurs before the action of $Q$, and this action is using the value of the counter.
+Remark that it includes a loop increasing the counter, occuring before the action of $Q$, and this action is using the value of the counter.
 Let us go into the details, using rules WT1/2/3.
@@
 \subsection{Running example}
-- If we already have shown the saturated relation, we only need to argue on bisimulation here.
+- In section \ref{} we have shown the full satured weak automaton for both the specification and the implementation of the simple protocol.
 
@@
 
+  \TODO{Eric: this is still ABP ! rewrite completely, baesd on saturation example 2 pages before.}
+
 The ``saturation'' step in the construction of the weak relation will
 pick all $\tau^*$ and $\tau^*;a;\tau^*$ sequences from the OA, and build a weak
-open trnsition from each sequence. Here is one example of a short sequence,
-starting with the open transition $OT_2$ of page \pageref{OT:ABP},
-then transmitting the message to the receiver (if the sender and
-receiver control bits are equal), and to the environment. The two
+open transition from each sequence. Here is one example of a short sequence,
+starting with the open transition $OT_1$ of page \pageref{OT:SimpleProt},
+then transmitting the message to the receiver, and to the environment. The two
 firsts open transitionTs are internal, the last one is visible, so it constitute a
@@
 
-\TODO{Eric: rewrite completely}
-\noindent
+noindent
      $  \openrule{
@@
     \ERIC{Apres simplification:}
+
 \medskip\noindent

### 2019-12-17 2016-Weak-FH-Bisim/WeakBisim.tex
2 todos et delimitation de l exemple

@@
 Two pNets are FH-bisimilar if there exist a relation between their associated 
-automata that is an FH-bisimulation and their initial states are in the relation (with some initial predicate).
-\TODO{check}
+automata that is an FH-bisimulation and their initial states are in the relation (i.e. the predicate associated with the initial states is verifiable).
+%\TODO{check}
 \end{definition}
@@
 We show on the top one possible sequence corresponding to a weak transition, on the bottom left the concerned subset of the original OA, and on the right the generated weak transition.
-\end{example}
 
@@
 
+\end{example}
+
   \begin{example}
@@
 \begin{definition}[Notation: Semantics of pNets as a weak open automaton]
-Let $A$ be the open automaton expressing the semantics of an open pNet $\pNet$; let $<J,\mathcal{S},s_0,  \WT>$ be the weak open automata derived from $A$.
-For any $\WOT\in\WT$, we denote $\pNet \models \WOT$, this defines the semantics of the pNet $\pNet$ as a weak open automaton.
-\TODO{strange sentence}
+Let $A$ be the open automaton expressing the semantics of an open pNet $\pNet$; let $<J,\mathcal{S},s_0,  \WT>$ be the weak open automaton derived from $A$; this weak open automaton defines the weak semantics of the pNet $\pNet$.
+Then, we denote $\pNet \models \WOT$ whenever $\WOT\in\WT$.
 \end{definition}

### 2019-12-19 2016-Weak-FH-Bisim/WeakBisim.tex

--- 2019-12-11 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 \paragraph{Example} Figure \ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the Specification pNet in Figure \ref{SimpleProt:Spec}. 
-
-%\TODO{:  and maybe one example on the Impl. OTs presented in latex readable form??}
-\TODO{Comment on Fig 3...}
+\RAB{Here, in the open automaton drawing, we use a user-friendly notation for the OTs, in the form ``$\{actions of holes\} [guard] action \{assigns\}$'', rather than the full OT form with the red-dotted rule.
+Note that the resulting action of the OTs appear here between the guard and the set of assignments.
+For example, in the OT where $\beta=\{P\mapsto p\_a\}$, $\Pred=P\_a\neq p\_send$, and $\alpha=P\_a$ is denoted in the open automata \texttt{\{P->p-a\} [P-a!=p-send] P-a}.
+}
 
@@
 Figure \ref{SimpleProtCounter:ImplOA} shows the full open automaton of the implementation $SimpleSystem$. 
-Here, in the open automaton drawing, we use a user-friendly notation for the OTs, in the form ``$\{actions of holes\} [guard] action \{assigns\}$'', rather than the full OT form with the red-dotted rule.
-Note that the resulting action of the OTs appear here betwen the guard and the set of assignments.
-Note that we have also simplified the form of the variable dependencies in the OTs, again for readability, replacing e.g.
-in OT1 $\{P\mapsto p\_send(m)\} \qquad [m=m']$ and $\alpha= \underline{in(m')}$ by the shorter \texttt{\{P->p\_send(m)\} in(m)}.
+Note that, again for readability,  we have also simplified the form of the variable dependencies in the OTs replacing e.g.
+in OT1 $\{P\mapsto p\_send(m)\} \quad [m=m']$ and $\alpha= \underline{in(m')}$ by the shorter \texttt{\{P->p\_send(m)\} in(m)}.
 

### 2019-12-19 2016-Weak-FH-Bisim/WeakBisim.tex
over skype

--- 2019-12-17 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 trivial). 
-We use \ERIC{sets of assignments of the form $x_i:=e_i$}, ranged over by $\Post$; $\subst{\Post}$ is the substitution that applies all the substitutions defined by $\Post$ in a parallel manner.
+We use sets of assignments of the form $x_i:=e_i$, ranged over by $\Post$; $\subst{\Post}$ is the substitution that applies all the substitutions defined by $\Post$ in a parallel manner.
 $\otimes$ is the composition operator on substitutions: $(x_k\gets e_k)^{k\in K}\shortotimes \Post =  (x_k\gets e_k\subst{\Post})^{k\in K}$
@@
         \Pred\ is a predicate over the source variables. \Post\ is a set of 
-	\ERIC{assignments that are effective \emph{after the open transition}}, they are
+	assignments that are effective \emph{after the open transition}, they are
         represented as a substitution of the form $({x_k\gets e_k})^{k\in K}$ 
@@
       $\openrule
-         {\gamma=\{\texttt{q-revc(ec)}\subst{ec\gets ec+n}\}, True,
+         {\{Q\mapsto\texttt{q-revc(ec)}\subst{ec\gets ec+n}\}, True,
 			\subst{ec\gets ec+n} }

### 2019-12-19 2016-Weak-FH-Bisim/WeakBisim.tex
remis removed part

@@
  \[  OT_1  = \openrule{
-      \{P\mapsto p\_send(m)\} \qquad [m=m'] \qquad \{s1\_m\gets m\}
-                      }
-    {\ostate{s_0,a_0,r_0} \OTarrow{\underline{in(m')}} \ostate{s_1,a_0,r_0}}
+      \{P\mapsto p\_send(m)\},  [m=m'],  \{s1\_m\gets m\}
+                      }
+    {\ostate{s_0,m_0,r_0} \OTarrow{\underline{in(m')}} \ostate{s_1,m_0,r_0}}
     \]
@@
 \paragraph{Example} Figure \ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the Specification pNet in Figure \ref{SimpleProt:Spec}. 
-
-%\TODO{:  and maybe one example on the Impl. OTs presented in latex readable form??}
-\TODO{Comment on Fig 3...}
+\RAB{Here, in the open automaton drawing, we use a user-friendly notation for the OTs, in the form ``$\{actions of holes\} [guard] action \{assigns\}$'', rather than the full OT form with the red-dotted rule.
+Note that the resulting action of the OTs appear here between the guard and the set of assignments.
+For example, in the OT where $\beta=\{P\mapsto p\_a\}$, $\Pred=P\_a\neq p\_send$, and $\alpha=P\_a$ is denoted in the open automata \texttt{\{P->p-a\} [P-a!=p-send] P-a}.
+}
 
 \begin{figure}[t]
-   \centerline{\includegraphics[width=9cm]{ATG/SPSpecOpen}}
+   \centerline{\includegraphics[width=11cm]{ATG/SPSpecOpen}}
    \caption{Specification OA (version with the error counter)}
@@
 Note that we have also simplified the form of the variable dependencies in the OTs, again for readability, replacing e.g.
-in OT1 $\{P\mapsto p\_send(m)\} \qquad [m=m']$ and $\alpha= \underline{in(m')}$ by the shorter \texttt{\{P->p\_send(m)\} in(m)}.
+in OT1 $\beta=\{P\mapsto p\_send(m)\}$ $\Pred=[m=m']$ and $\alpha= \underline{in(m')}$ by the shorter \texttt{\{P->p\_send(m)\} in(m)}.
 

### 2020-01-03 2016-Weak-FH-Bisim/WeakBisim.tex
nouvelle figure 5 en page 23

@@
 The return $ack$ message from $receiver$ to $sender$ is supposed to be safe.
-The final transmission of the message to the recipient (Hole Q) include the value of the ``error counter'' $ec$.
+The final transmission of the message to the recipient (the hole Q) includes the value of the ``error counter'' $ec$.
 
@@
 For instance, in the vector "$< p\_send(m),in(m),\_> \rightarrow \underline{in(m)}$ only $P$ and {\it PrefectMedium} nodes are involved in the synchronization.
-In particular, this means the synchronization between these processes occurs when  process $P$  performs $p\_send(m)$  action sending a message, and  the medium accepts the message through $in(m)$ action  at the same time.
+More precisely, the synchronization between these processes occurs when  process $P$  performs $p\_send(m)$  action sending a message, and  the medium accepts the message through $in(m)$ action  at the same time.
 And the result that will be returned at upper level is the internal action  $\underline{in(m)}$.
@@
 \begin{figure}[t]
-   \includegraphics[width=5.5cm]{XFIG/SimpleProt-Schema}
-   \includegraphics[width=6.5cm]{XFIG/SimpleProt2-Spec}
+   \includegraphics[width=5cm]{XFIG/SimpleProt-Schema}
+   \includegraphics[width=7cm]{XFIG/SimpleProt2-Spec}
    \caption{Specification pNet Schema and Specification}
@@
 
+\TODO{J'ai un probleme ici, comme on a dit que les AO etaient satures par substitution, ils sont par nature infinis...
+Donc le theoreme, tel qu'il est exprime, est vrai, mais inapplicable.
+La solution est dans le papier de PEPM, mais complique a expliquer...}
+\TODO{pour faire simple, on vire le theoreme, et on met une simple note disant qu'on a une definition dans PEPM d'une description structurelle finie, et un algo avec terminaison ?}
+
 If we assume that everything is finite (states and transitions in the
@@
 In this translation, the states of the open automata are obtained from the states of the pLTSs at the leaves of the composition.
-The predicates on the transition is obtained both from the predicates on the pLTSs transitions and from the synchronisation vectors involved in the transition.
+The predicates on the transitions are obtained both from the predicates on the pLTSs transitions and from the synchronisation vectors involved in the transition.
+\TODO{Meme remarque ici, on ne genere qu'une representation finie des OAs}
 
@@
 
+\begin{figure}[ht]
+   \centerline{\includegraphics[width=11cm]{ATG/SPSpecOpen}}
+   \caption{Specification OA}
+   \label{SimpleProtCounter:SpecOA}
+\end{figure}
+
 \paragraph{Example} Figure \ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the Specification pNet in Figure \ref{SimpleProt:Spec}. 
@@
 Note that the resulting action of the OTs appear here between the guard and the set of assignments.
-For example, in the OT where $\beta=\{P\mapsto p\_a\}$, $\Pred=P\_a\neq p\_send$, and $\alpha=P\_a$ is denoted in the open automata \texttt{\{P->p-a\} [P-a!=p-send] P-a}.
-}
-
-\begin{figure}[t]
-   \centerline{\includegraphics[width=11cm]{ATG/SPSpecOpen}}
-   \caption{Specification OA (version with the error counter)}
-   \label{SimpleProtCounter:SpecOA}
-\end{figure}
-
-Figure \ref{SimpleProtCounter:ImplOA} shows the full open automaton of the implementation $SimpleSystem$.
-Here, in the open automaton drawing, we use a user-friendly notation for the OTs, in the form ``$\{actions of holes\} [guard] action \{assigns\}$'', rather than the full OT form with the red-dotted rule.
-Note that the resulting action of the OTs appear here betwen the guard and the set of assignments.
-Note that we have also simplified the form of the variable dependencies in the OTs, again for readability, replacing e.g.
-in OT1 $\beta=\{P\mapsto p\_send(m)\}$ $\Pred=[m=m']$ and $\alpha= \underline{in(m')}$ by the shorter \texttt{\{P->p\_send(m)\} in(m)}.
-
-    \begin{figure}[h]
+For examplein the upper left of the figure, the OT where $\beta=\{P\mapsto p\_a\}$, $\Pred=[\forall m.
+P\_a\neq p\_send(m)]$, and $\alpha=P\_a$ is denoted as ``\texttt{\{P->p-a\} [Forall m.P-a!=p-send(m)] P-a}''.
+}
+
+    \begin{figure}[ht]
   \centerline{\includegraphics[width=10cm]{ATG/SPImplOpen}}
@@
 
-%% We show here the first open transition, written here in the form of the tool full output.
-
-%% $  OT_1  = \openrule{
-%%   (P\mapsto p\_send(m:sva\_SV6:1:1)) \\
-%%   [( msg =m: sva\_SV6 :1:1) \wedge (( in( msg ))=( in(m: sva_SV6 :1:1)))]\\
-%%   \{ s1\_msg := msg , s1\_c := 0\}
-%%                       }
-%% {\ostate{s_0,m_0,r_0} \OTarrow{\underline{in(m:sva\_SV6:1:1)}} \ostate{s_1,m_0,r_0}}
-%% $
-    \ERIC{Also we have short labels for states, representing $\ostate{s_0,m_0,r_0}$ by \texttt{000}.
+    Figure \ref{SimpleProtCounter:ImplOA} shows the open automaton of the implementation $SimpleSystem$.
+    \ERIC{In this drawing, we have short labels for states, representing $\ostate{s_0,m_0,r_0}$ by \texttt{000}.
+For readability we only have written the \emph{external} actions of holes $P$ and $Q$ on the loop transitions of the first staes; they are also present on all other states.
 The resulting behavior is quite simple: In every state, holes $P$ and $Q$ can do any action independent of the protocol (we only have labelled these on state \texttt{000}).
@@
 In most of the transitions, you can observe that data is propagated between the successive state variables (holding the message, and the error counter value).
-On th eright of the figure, you have a loop of $\tau$ transitions showing the handling of errors and corresponding increments of the error counter.}
+On the right of the figure, you have a loop of $\tau$ transitions showing the handling of errors and corresponding increments of the error counter.}
     \TODO{j'ai comment\'e Fig 3, vous pouvez relire ?}
@@
 
+%% \begin{figure}[ht]
+%%    \centerline{\includegraphics[width=11cm]{ATG/WOT2}}
+%%   \caption{Construction of WOT2}
+%%    \label{WOT2}
+%% \end{figure}
+
 \begin{figure}[ht]
-   \centerline{\includegraphics[width=11cm]{ATG/WOT2}}
+   \centerline{\includegraphics[width=8cm]{XFIG/WOT2-result}}
   \caption{Construction of WOT2}
@@
 \begin{example}
-  Figures \ref{WOT2} shows the construction of one of the weak transitions of the Specification OA.
-We show on the top one possible sequence corresponding to a weak transition, on the bottom left the concerned subset of the original OA, and on the right the generated weak transition.
-
-%  In the case of WOT1, we start with a tau loop, then change state with an action of hole $P$ to state 1, initializing the $ec$ counter.
-On state 1, we have two tau loops, on of them increasing the $ec$ counter.
-The resulting weak transition is represented here as a regular expression including assignemnts, rather than the substitutions of the formal definition.
-It can the be abbreviated as: $P\mapsto \texttt{p-send}\ \{(ec:=ec+1)^*$.
+  Figure \ref{WOT2} shows the construction of one of the weak transitions of the Specification OA.
+We show on the top the subset of the original open automaton (from Figure \ref{SimpleProtCounter:SpecOA}) consider here, and at the bottom the generated weak transition.
 
@@
 Let us go into the details, using rules WT1/2/3.
-For simplification we ignore the pure $\tau$-loops before and after the central \texttt{q-recv(ec)} action, they have no effect on the construction.
 First consider application of Rule WT3 on the first 3 transitions.

### 2020-01-03 2016-Weak-FH-Bisim/WeakBisim.tex
nettoyages divers

@@
 
-\TODO{Explain the partial OA}
+\TODO{Eric: Explain the partial OA}
 \end{example}
@@
 \subsection{Weak FH-bisimulation}
-For defining a bisimulaiton relation between weak open automatas, two options are possible.
+For defining a bisimulation relation between weak open automata, two options are possible.
 Either we define a simulation similar to the strong simulation but based on open automata, this would look like the FH-simulation but would need to be adapted to weak open transitions.
@@
 
-Two pNets are weak FH-bisimilar if there exist a relation between their associated 
+Two pNets are weak FH-bisimilar if there exists a relation between their associated 
 automata that is a Weak FH-bisimulation and their initial states are in the relation, i.e. 
@@
     \bigskip
-    \ERIC{Anciennes versions:}
-$\ostate{1000}\OTarrow{\underline{send(m,b)}, \phi_1 = [x=s_1\_b \land
-    m=s_1\_m]}\ostate{2100}$\\
-and $\qquad\ostate{2100}$ variable assignments are: $\psi_1 = \{m_1\_m:=m; m_1\_x:=x; s_2\_b:=s_1\_b\}$;\\
-\\
-$\ostate{2100}\OTarrow{\tau <m\_send(m_1\_m,m_1\_x), r\_rec(?m',?b)>,
-  \phi_2 = [r_0\_b=b \land m'=m_1\_m \land b=m_1\_x]}\ostate{2001}$\\
-and $\qquad\ostate{2001}$ assignments: $\psi_2 = \{r_1\_b:=r_0\_b; r_1\_m:=m;
-; s_2\_b:=s_1\_b\}$;\\
-\\
-$\ostate{2001}\OTarrow{v,
-  \phi_3 = [v=out(r_1\_m)]}\ostate{2002}$\\
-and $\qquad\ostate{2002}$ variablesassignments: $\psi_3 = \{r_2\_b:=r_1\_b; s_2\_b:=s_1\_b\}$;\\
+    ...
+    \bigskip
 
@@
 \ERIC{
-=> Context VCE, ref to FASE paper\\
-=> Current prototype: programatic creation of pNet objects, through the pNet API in VCE. On the middle term, this should be compiled from some language or graphical formalism.\\
-=> Open transitions are computed as a direct implementation of the algorithm above.
-Steps 2a-2b are merged: at each pNet node, after application of rule \TrDeux, the resulting OT is built from the premisses, without explicitely constructing the deduction tree.
-\\
-=> Variable names are generated for all ``fresh'' and ``clone'' operations, using structured variable names ensuring uniqueness of fresh names, but also reasonable readability of these names for debugging purposes.\\
-=> Satisfiability check is done only at toplevel of the deduction tree construction.
-An alternative would be to submit the satisfiability check to the SMT solver at each level of the tree construction, potentialy reducing the overall number of combinations.
-But submission to the SMT engine is costly, and more complexity analysis is required before deciding if this would be worthwhile.\\
+  => Context VCE, ref to FASE paper, citer Avocs et  PEPM\\
 => Simplification is mostly implemented. It is not strictly required for the Open Automaton construction, but it will be critical later for predicate comparison in the bisimulation algorithm.}
-
-Independently, it is clear that most interesting properties of
-such complex systems will not be provable by strong bisimulation.
-Next steps will include the investigation of weak
-versions of the FH-bisimulation, using the notion of
-\emph{synchronised actions} mentionned in the paper.
-%We are convinced that this work will contribute to the design of tools for
-%verifying open distributed systems.
 
@@
 
-\begin{figure}[t]
-   \includegraphics[width=5.5cm]{XFIG/SimpleProt-Schema}
-   \includegraphics[width=6.5cm]{XFIG/SimpleProt2-Spec}
-   \caption{Specification pNet Schema and Specification}
-   \label{App:SimpleProt:Spec}
-
-\end{figure}
-
-\begin{figure}[t]
-  \centerline{\includegraphics[width=12cm]{XFIG/SimpleProt2-pNet}}
-  \caption{Composed pNet with the Simple Protocol Implementation}  \label{App:SimpleProt:Impl}
-\end{figure}
+%% \begin{figure}[t]
+%%    \includegraphics[width=5.5cm]{XFIG/SimpleProt-Schema}
+%%    \includegraphics[width=6.5cm]{XFIG/SimpleProt2-Spec}
+%%    \caption{Specification pNet Schema and Specification}
+%%    \label{App:SimpleProt:Spec}
+
+%% \end{figure}
+
+%% \begin{figure}[t]
+%%   \centerline{\includegraphics[width=12cm]{XFIG/SimpleProt2-pNet}}
+%%   \caption{Composed pNet with the Simple Protocol Implementation}  \label{App:SimpleProt:Impl}
+%% \end{figure}
 
 The first piece of code is the textual definition of the SimpleProtSec
-pNet. This code should be intuitive enough to read, with the following
-conventions:
+pNet, that was drwan in Figure \ref{SimpleProt:Impl}, page \pageref{SimpleProt:Impl}. This code should be intuitive enough to read, with the following
+conventions, that brings some user-friendly features that are maps by the editor into pure pNet constructs.
 
@@
     here.
-  \item \TODO{continue...}
+  \item the variables in the guards of synchronisation vectors do not need to be explicitely quantified: all variable in a guard that does not appear inside the vector actions will be recognised as bound by a \emph{foral} quantifier inside the guard.
+    \item the tools will check that everything is correctly declared, and that variables are used properly, that vectors have coherent length, etc.
 \end{itemize}
 
-\TODO{keep ?}
-\paragraph{Variable management.}
-The variables in each synchronisation vector are considered local:
-for a given pNet expression, we must have fresh local variables for
-each occurrence of a vector (i.e. each time we instantiate rule
-\TrDeux). Similarly the state variables of each copy of a
-given pLTS in the system, must be distinct, and those created for each
-application of \TrDeux\ have to be fresh and all distinct. 
-This is implemented within the open-automaton generation algorithm,
-using name generation using a global counter as a suffix.
+%% \TODO{keep ?}
+%% \paragraph{Variable management.}
+%% The variables in each synchronisation vector are considered local:
+%% for a given pNet expression, we must have fresh local variables for
+%% each occurrence of a vector (i.e. each time we instantiate rule
+%% \TrDeux). Similarly the state variables of each copy of a
+%% given pLTS in the system, must be distinct, and those created for each
+%% application of \TrDeux\ have to be fresh and all distinct. 
+%% This is implemented within the open-automaton generation algorithm,
+%% using name generation using a global counter as a suffix.
 
@@
 
-From this code,A more compact view (maybe more readable ???) is given
-by the pretty-printer of VerCors:
-
-\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
-SimpleProtImpl2
---------------------
-SV6 SVs: <p_send(m), in(m), _>-->in(m)
-SV7 SVs: <p_a, _, _>-->p_a, p_a!=(p_send(m))
-SV8 SVs: <_, out(m, c), q_recv(m, c)>-->out(m, c)
-SV9 SVs: <_, _, q_a>-->q_a, q_a!=(q_recv(m, c))
-SV11 SVs: <_, _tau_, _>-->_tau_
-Holes: P
-Subnets: medium
-- medium
-- SV0 SVs: <in(m), _, _>-->in(m)
-- SV1 SVs: <s_send(m, c), m_recv(m, c), _>-->_tau_
-- SV2 SVs: <_, m_send(m), r_recv(m)>-->_tau_
-- SV3 SVs: <s_ack, _, r_ack>-->_tau_
-- SV4 SVs: <s_error, m_error, _>-->_tau_
-- SV5 SVs: <_, _, out(m, c)>-->out(m, c)
-- SV10 SVs: <_, _tau_, _>-->_tau_
-- pLTS: Sender
-- - Transition: s0---in(msg)-->s1, { s1_msg := msg s1_c := 0}
-- - Transition: s1---s_send(s1_msg, s1_c)-->s2, {}
-- - Transition: s2---s_ack-->s0, {}
-- - Transition: s2---s_error-->s1, { s1_c := s2_c+1}
-- - Variable: s1_c, State: s1, Value(s) = 0,s2_c+1,
-- - Variable: s1_msg, State: s1, Value(s) = msg,
-- pLTS: M1
-- - Transition: a0---m_recv(msg, c)-->a1, { a1_msg := msg a1_c := c}
-- - Transition: a1---m_send(a1_msg, a1_c)-->a0, {}
-- - Transition: a1---_tau_-->a2, {}
-- - Transition: a2---m_error-->a0, {}
-- - Variable: a1_msg, State: a1, Value(s) = msg,
-- - Variable: a1_c, State: a1, Value(s) = c,
-- pLTS: Receiver
-- - Transition: r0---r_recv(msg, c)-->r1, { r1_msg := msg r1_c := c}
-- - Transition: r1---out(r1_msg, r1_c)-->r2, {}
-- - Transition: r2---r_ack-->r0, {}
-- - Variable: r1_msg, State: r1, Value(s) = msg,
-- - Variable: r1_c, State: r1, Value(s) = c,
-Holes: Q
-\end{lstlisting}
+%% From this code,A more compact view (maybe more readable ???) is given
+%% by the pretty-printer of VerCors:
+
+%% \begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
+%% SimpleProtImpl2
+%% --------------------
+%% SV6 SVs: <p_send(m), in(m), _>-->in(m)
+%% SV7 SVs: <p_a, _, _>-->p_a, p_a!=(p_send(m))
+%% SV8 SVs: <_, out(m, c), q_recv(m, c)>-->out(m, c)
+%% SV9 SVs: <_, _, q_a>-->q_a, q_a!=(q_recv(m, c))
+%% SV11 SVs: <_, _tau_, _>-->_tau_
+%% Holes: P
+%% Subnets: medium
+%% - medium
+%% - SV0 SVs: <in(m), _, _>-->in(m)
+%% - SV1 SVs: <s_send(m, c), m_recv(m, c), _>-->_tau_
+%% - SV2 SVs: <_, m_send(m), r_recv(m)>-->_tau_
+%% - SV3 SVs: <s_ack, _, r_ack>-->_tau_
+%% - SV4 SVs: <s_error, m_error, _>-->_tau_
+%% - SV5 SVs: <_, _, out(m, c)>-->out(m, c)
+%% - SV10 SVs: <_, _tau_, _>-->_tau_
+%% - pLTS: Sender
+%% - - Transition: s0---in(msg)-->s1, { s1_msg := msg s1_c := 0}
+%% - - Transition: s1---s_send(s1_msg, s1_c)-->s2, {}
+%% - - Transition: s2---s_ack-->s0, {}
+%% - - Transition: s2---s_error-->s1, { s1_c := s2_c+1}
+%% - - Variable: s1_c, State: s1, Value(s) = 0,s2_c+1,
+%% - - Variable: s1_msg, State: s1, Value(s) = msg,
+%% - pLTS: M1
+%% - - Transition: a0---m_recv(msg, c)-->a1, { a1_msg := msg a1_c := c}
+%% - - Transition: a1---m_send(a1_msg, a1_c)-->a0, {}
+%% - - Transition: a1---_tau_-->a2, {}
+%% - - Transition: a2---m_error-->a0, {}
+%% - - Variable: a1_msg, State: a1, Value(s) = msg,
+%% - - Variable: a1_c, State: a1, Value(s) = c,
+%% - pLTS: Receiver
+%% - - Transition: r0---r_recv(msg, c)-->r1, { r1_msg := msg r1_c := c}
+%% - - Transition: r1---out(r1_msg, r1_c)-->r2, {}
+%% - - Transition: r2---r_ack-->r0, {}
+%% - - Variable: r1_msg, State: r1, Value(s) = msg,
+%% - - Variable: r1_c, State: r1, Value(s) = c,
+%% Holes: Q
+%% \end{lstlisting}
 

### 2020-01-07 2016-Weak-FH-Bisim/WeakBisim.tex
pages 23-24

@@
 For readability we only have written the \emph{external} actions of holes $P$ and $Q$ on the loop transitions of the first staes; they are also present on all other states.
-The resulting behavior is quite simple: In every state, holes $P$ and $Q$ can do any action independent of the protocol (we only have labelled these on state \texttt{000}).
-Then we have a main loop including receiving a message from $P$ and transmitting the same message to $Q$, with some intermediate $\tau$ actions from the internal communications between the protocol processes.
+The resulting behavior is quite simple:  we have a main loop including receiving a message from $P$ and transmitting the same message to $Q$, with some intermediate $\tau$ actions from the internal communications between the protocol processes.
 In most of the transitions, you can observe that data is propagated between the successive state variables (holding the message, and the error counter value).
 On the right of the figure, you have a loop of $\tau$ transitions showing the handling of errors and corresponding increments of the error counter.}
-    \TODO{j'ai comment\'e Fig 3, vous pouvez relire ?}
 
@@
 \begin{figure}[ht]
-   \centerline{\includegraphics[width=8cm]{XFIG/WOT2-result}}
+   \centerline{\includegraphics[width=7cm]{XFIG/WOT2-result}}
   \caption{Construction of WOT2}
@@
   Figure \ref{WOT2} shows the construction of one of the weak transitions of the Specification OA.
-We show on the top the subset of the original open automaton (from Figure \ref{SimpleProtCounter:SpecOA}) consider here, and at the bottom the generated weak transition.
+On the top we show the subset of the original open automaton (from Figure \ref{SimpleProtCounter:SpecOA}) considered here, and at the bottom the generated weak transition.
 
   WOT2 here is the transition delivering the result of the algorithm to hole $Q$.
-Remark that it includes a loop increasing the counter, occuring before the action of $Q$, and this action is using the value of the counter.
+Remark that it includes a loop increasing the error counter, occuring before the action of $Q$, and this action is using the resulting value of the counter.
 Let us go into the details, using rules WT1/2/3.
-First consider application of Rule WT3 on the first 3 transitions.
+First WT1 adds a $\tau$ loop on each state.
+Then consider application of Rule WT3 on a sequence 3 internal actions ``$\tau\subst{ec\gets ec+1};\tau\subst{ec\gets ec+1};\tau$''.
 Hole actions and predicates are empty, we just concentrate on the Post operations.
@@
   $\openrule
-         {\set{\tau}, True,
+         {\{\}, True,
 			\subst{\texttt{ec++}\shortotimes\texttt{ec++}\shortotimes\emptyset} }
@@
   $\openrule
-         {\emptyset, True,
+         {\{\}, True,
 			\subst{ec\gets ec+2} }
@@
 			\subst{ec\gets ec+n} }
-         {s \OTWeakarrow {\texttt{q-recv(ec)}\subst{ec\gets ec+n}} s'}$
-
+         {s \OTWeakarrow {\texttt{out(m,ec)}\subst{ec\gets ec+n}} s'}$
 \end{example}
@@
   \begin{example}
-    Figure \ref{SimpleProtCounter:WeakSpecOA} shows the weak automaton of the simple protocol specification.
+    Figures \ref{SimpleProtCounter:WeakSpecOA} and \ref{SimpleProtCounter:SpecOA-partial} respectively show the weak automata of the simple protocol specification and implementation.
     \TODO{comment...}
@@
    \centerline{\includegraphics[width=10cm]{ATG/SPSpecWeakOpen}}
-  \caption{Weak Open Automaton of the Specification}
+  \caption{Weak Open Automaton of the Specification \TODO{out of date}}
    \label{SimpleProtCounter:WeakSpecOA}
@@
 
-  \begin{example}
-  Figure \ref{SimpleProtCounter:SpecOA-partial} shows a partial view of the weak automaton of the simple protocol implementation.
-
-\TODO{Eric: Explain the partial OA}
-\end{example}
-
 \begin{figure}[t]
    \centerline{\includegraphics[width=12cm]{ATG/SPImplWeakOpen}}
-  \caption{Weak Open Automaton of the implementation, partial}
+  \caption{Weak Open Automaton of the implementation, \TODO{partial, can we show it in full ?}}
    \label{SimpleProtCounter:SpecOA-partial}
@@
 
+\newpage
 \subsection{Composition properties: composition of weak open transitions}

### 2020-01-08 2016-Weak-FH-Bisim/WeakBisim.tex
pepm et argument subst

--- 2020-01-03 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
+\LUDO{I added this paragraph}
+Because of the semantic interpretation of open automata, the set of open transition of an open automaton is infinite (for example because every free variable can be renamed).
+However an open automaton is characterized by a  subset of these open transition which is sufficient to generate, by substitution the other ones.
+In the following, we will abusively write that we define an ``open automaton'' when we provide only the set of open transitions that is sufficient to generate a proper open automaton by saturating each open transition by all possible substitutions.
+
 Another consequence of the semantics and logical interpretation of the
@@
 \TODO{pour faire simple, on vire le theoreme, et on met une simple note disant qu'on a une definition dans PEPM d'une description structurelle finie, et un algo avec terminaison ?}
-
+\TODO{[LUDO->ERIC] D'accord: tu ecris comme tu connais le mieux le papier PEPM?}
 If we assume that everything is finite (states and transitions in the

### 2020-01-10 2016-Weak-FH-Bisim/WeakBisim.tex
dur dur le WOA
figures

@@
 It acts as the parallel operator.
-It consists of tree nodes: two Holes $P$ and $Q$ and one subnet, noted {\it PrefectMedium}.
+It consists of tree nodes: two Holes $P$ and $Q$ and one subnet, noted {\it PrefectBuffer}.
 Nodes of the tree are synchronized using four synchronization vectors, that  express the possible synchronization between the parameterized actions of a subset of the nodes.
-For instance, in the vector "$< p\_send(m),in(m),\_> \rightarrow \underline{in(m)}$ only $P$ and {\it PrefectMedium} nodes are involved in the synchronization.
+For instance, in the vector "$< p\_send(m),in(m),\_> \rightarrow \underline{in(m)}$ only $P$ and {\it PrefectBuffer} nodes are involved in the synchronization.
 More precisely, the synchronization between these processes occurs when  process $P$  performs $p\_send(m)$  action sending a message, and  the medium accepts the message through $in(m)$ action  at the same time.
@@
 
+\begin{figure}[ht]
+   \centerline{\includegraphics[width=10cm]{XFIG/SPSpecOpen}}
+   \caption{Specification OA}
+   \label{SimpleProtCounter:SpecOA}
+\end{figure}
+
 \paragraph{Example} Figure \ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the Specification pNet in Figure \ref{SimpleProt:Spec}. 
@@
 In the same manner, $\Pred_3$ must be applied the joint substitution $\Post_2\bigotimes\Post_1$.
-Similarly, effects on variables must be applied to obtain the global effect of the composed weak open transition, it must also be applied to observable actions of the holes, and to the global action of the weak open transition	.
+Similarly, effects on variables must be applied to obtain the global effect of the composed weak open transition, it must also be applied to observable actions of the holes, and to the global action of the weak open transition.
 

### 2020-01-14 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf paper: minor revisions following latest reviews

@@
   more flexibility in the acceptable behaviours.  In other words, this
-  modification enforces essentially the same properties, while
+  modification enforces similar properties, while
   discarding less acceptable behaviours.
@@
 show that they do impose corresponding properties.
-Safety of the system is obtained compositionally, whereas liveness is verified by checking \emph{pair-wise} non-interference.
-In both cases, the main characteristic of the approach is compsitionality, so we can compute the behavior and analyse the properties on \emph{small open systems}, and use these properties independently when composing bigger systems.
+Safety of the system is obtained compositionally, whereas liveness is verified by checking \emph{pair-wise} non-interference \cite{AttieBBJS16-architectures-faoc}.
+In both cases, the main characteristic of the approach is compositionality, so we can compute the behavior and analyse the properties on \emph{small open systems}, and use these properties independently when composing bigger systems.
 %

### 2020-01-14 2016-Weak-FH-Bisim/WeakBisim.tex
ajout fig

@@
 Note that the resulting action of the OTs appear here between the guard and the set of assignments.
-For examplein the upper left of the figure, the OT where $\beta=\{P\mapsto p\_a\}$, $\Pred=[\forall m.
+For example in the upper left of the figure, the OT where $\beta=\{P\mapsto p\_a\}$, $\Pred=[\forall m.
 P\_a\neq p\_send(m)]$, and $\alpha=P\_a$ is denoted as ``\texttt{\{P->p-a\} [Forall m.P-a!=p-send(m)] P-a}''.
@@
   \centerline{\includegraphics[width=10cm]{ATG/SPImplOpen}}
+  \caption{Open Automaton of the Simple Protocol Implementation}  \label{SimpleProtCounter:ImplOA}
+\end{figure}
+
+    \begin{figure}[ht]
+  \centerline{\includegraphics[width=10cm]{XFIG/SPImplOpen}}
   \caption{Open Automaton of the Simple Protocol Implementation}  \label{SimpleProtCounter:ImplOA}
@@
 
-\begin{figure}[ht]
+\begin{figure}[h]
    \centerline{\includegraphics[width=10cm]{ATG/SPSpecWeakOpen}}
@@
 
-\begin{figure}[t]
-   \centerline{\includegraphics[width=12cm]{ATG/SPImplWeakOpen}}
-  \caption{Weak Open Automaton of the implementation, \TODO{partial, can we show it in full ?}}
+\begin{figure}[h]
+   \centerline{\includegraphics[width=9cm]{XFIG/SimpleProtImpl-WOA}}
+  \caption{Weak Open Automaton of the implementation}
    \label{SimpleProtCounter:SpecOA-partial}
 \end{figure}
+
+\TODO{Eric: insert here a table with the details of the WOTs...}
+
+\smallskip
+$1^st$ try, user-friendly style:
+
+$$ 3 = \tau^*; \underline{in(m)}\{s1\_c:=0, s1\_m:=m\}; \tau\{s1\_c++\}^*$$
+
+\smallskip
+$2^nd$ try, full formal style ?:
+
+$$ 1 = \openrule
+         {\{P\mapsto\texttt{p-a}\}, [\forall m.p-a!=P\_send(m)], () }
+         {000 \OTWeakarrow {\texttt{p-a}} 000}$$
+\\
+$$6 = \openrule
+         {\{\}, [True], () }
+         {100 \OTWeakarrow {\tau\big(\subst{m1\_c:=s1\_c,m1\_m:=s1\_m,s2\_c:=s1\_c}\subst{s1\_c:=s2\_c+1}\big)^* \subst{m1\_c:=s1\_c,m1\_m:=s1\_m,s2\_c:=s1\_c} } 210}
+         $$
 

### 2020-01-16 2017-Xudong-SMT/ActaInformatica.tex
Upload a document reviewer2.docx. And Typos.

@@
 \newcommand{\YX}[1]{{#1}}
+\newcommand{\QINX}[1]{\textcolor{orange}{#1}}
 
@@
 
-\institute{Xudong Qin(\email{marsxd@gmail.com}) \and
-  Zechen Hou (\email{zechen@sei.ecnu.edu.cn}) \and
+\institute{Xudong Qin(\email{52174501019@stu.ecnu.edu.cn}) \and
+  Zechen Hou (\email{51174500089@stu.ecnu.edu.cn}) \and
   Yuxin Deng (\email{yxdeng@sei.ecnu.edu.cn}) \and
@@
 	generated by the algorithm.
-	\item We define a strategy checking satisfiability of open transitions in the course of the residual algorithm, and show the correctness of the optimised algorithm w.r.t. the original one.
+	\item We define a strategy checking satisfiability of open transitions \QINX{during the execution of} the residual algorithm, and show the correctness of the optimised algorithm.
+\QINX{Meanwhile its result is equivalent to the original one.}
+	% w.r.t. the original one.
 	% the reachable part of the open automaton can be generated and it is minimal with respect to the decidability of predicate satisfiability.
@@
 \begin{example}[The ``Enable'' Operator]\label{example:EnableOperator}
-\ERIC{In Fig. \ref{schema:enable-pnets} we give two possible pNet  encodings of the ``Enable'' operator, \YX{which are  state-oriented and data-oriented, respectively.} 
+\ERIC{In Fig. \ref{schema:enable-pnets} \QINX{we give the pNet encoding of the ``Enable'' operator in two different styles,} \YX{which are  state-oriented and data-oriented, respectively.} 
 The first one is called $EnableState$, and uses a controller $CState$ with three simple control actions, $l, r$ and $\delta$,  to synchronise the behaviour of $P$ and $Q$.
@@
 
-\ERIC{This shows an example of the generic $\texttt{FUN}$ constructor used to construct expressions (of the Action sort, or of any data sort) in any algebra presentations.
-  Here \texttt{FUN} will be instanciated e.g. as, $\delta(x)$ in the form of $\texttt{FUN}_{Action, Data}(\delta, x)$ where $x$ is a variable of type $Data$.
+\QINX{It shows an example that the generic $\texttt{FUN}$ constructor can be used to construct expressions (of the Action sort, or of any data sort) in any algebra presentations.
+  Here \texttt{FUN} will be \QINX{instantiated} e.g. as $\delta(x)$ in the form of $\texttt{FUN}_{Action, Data}(\delta, x)$ where $x$ is a variable of type $Data$.
   %Here we have $arity(\texttt{FUN}_{Action, Data})=2$ and $\texttt{FUN}_{Action, Data}: Action, Data\to Action$.
@@
 
-\ERIC{The $EnableData$ pNet uses the same algebra presentation.}\QIN{The main difference between $EnableState$ and $EnableData$ lies in the construction of their controllers $CState$ and $CData$ that we will discuss in the next section.}
-%\QIN{
-%Another possible encoding of such ``Enable'' operator, called $EnableData$, uses a data-oriented style, with a single state controller $CData$, and a state-variable $v$, with values in $\{0,1\}$.
-As there is no more constructor required, we can use the same algebra presentation as $EnableState$ in this case.
-%}
+\ERIC{The $EnableData$ pNet uses the same algebra presentation.} \QIN{The main difference between $EnableState$ and $EnableData$ lies in the construction of their controllers $CState$ and $CData$ that we will discuss in the next section.}
 \end{example}
@@
 do not have valid ground instantiations. This is not logically
-incorrect, but is naturally not an optimal representation. So (line 11) we prune
+incorrect, but is \QINX{clearly} not an optimal representation. So (line 11) we prune
 these UNSAT transitions: at the end of the open automaton generation,
@@
 algorithm (lines 12-14) builds the final open automaton via a traversal of $L1$,
-starting at the initial state $InitState(p)$ as defined in
-page~\pageref{def-states}. More precisely, this is a residual
-algorithm building a graph from the reachable transitions in $L1$. 
+starting at the initial state $InitState(p)$.
+%as defined in page~\pageref{def-states}
+More precisely, this is a residual algorithm building a graph from the reachable transitions in $L1$. 
 %and states are the set of target states of the transitions. 
@@
  managed by the two algorithms both are subsets of the cartesian
- product of the PLTS states, as defined in page \pageref{def-states}. In a
- similar way, the set of state variables attached to each state are
+ product of the PLTS states.
+ %, as defined in page \pageref{def-states}. 
+ In a similar way, the set of state variables attached to each state are
  also equal. Comparing  
@@
 
-Figure~\ref{schema:smt-lib} shows the translation of  Example~\ref{schema:unsat-ot}, page \pageref{schema:unsat-ot},
+Figure~\ref{schema:smt-lib} shows the translation of  Example~\ref{schema:unsat-ot} %,page \pageref{schema:unsat-ot},
 in the SMTlib syntax. It contains the declaration
@@
 %
-This translation ensures that no runtime error will occur
-in the SMT engine.
+This translation ensures that \QINX{the error occurred will not be caused by the incorrect inputs.}
+%no runtime error will occur in the SMT engine.
 
@@
 For this example, the tool (using Algorithm~\ref{alg1}) builds 408 open transitions, whereof 396
-are detected unsatisfiable by Z3.  The resulting open automaton, with
+are detected unsatisfiable by Z3. \QINX{According to the unsatisfiable transitions, there are 3 states which are not reachable.} The resulting open automaton, with
 3 reachable global states (out of the possible 6) and 12 open
@@
 To this end, we encode into Z3 the representations of the action algebra and
-the predicates before submitting them to the
-Z3 solver. 
+the predicates\QINX{, and then we submit them to the Z3 solver.}
 %
@@
 much as possible, only the reachable part of the open automaton. The
-handling of assignments makes the reachable computation more
+handling of assignments makes \QINX{the computation of the reachable states} more
 challenging. We show that the result is equivalent to the original

### 2020-01-17 2017-Xudong-SMT/ActaInformatica.tex
Add Alg.3 and Alg.4 according to the 2nd comment of Reviewer #1.

@@
 \State $\mathit{OA_1^0}$=\textit{makeReachableSubAutomaton}($\mathit{InitState}(P),L1)$;
-\Repeat $\mathit{OA_1^n}$=\textit{RefineReachableSubAutomaton}($\mathit{OA_1^{n-1}}$)
+\Repeat $\mathit{OA_1^n}$=\textit{refineReachableSubAutomaton}($\mathit{OA_1^{n-1}}$)
 \Until  $\mathit{OA_1^n}=\mathit{OA_1^{n-1}}$;   \hfill $\setminus \setminus$ Fixed point reached
@@
 \Require a pNet node $P$ with subnets $\overline{sn}$ and holes $\overline{hole}$; a global state $S$.
-\State Initialize empty list $l$ and set $L$ for sub-transitions and transitions, respectively;
+\State Initialize an empty list $l$ and a set $L$ for sub-transitions and transitions, respectively;
 	\For{each $\mathit{Subnet}$ in $\overline{sn}$}
@@
 In Algorithm~\ref{alg1}, functions \textit{filterUnsatTransitions} (in line 11) 
-\textit{RefineReachableSubAutomaton} (in line 13) make use of the Z3 engine to implement the
+\textit{refineReachableSubAutomaton} (in line 13) make use of the Z3 engine to implement the
 satisfiability checking, for all the OTs computed that far.
@@
 
-\QIN{As the removal of the unsatisfiable transitions \YX{may entail some transitions without preceeding} transitions, }
+\QIN{As the removal of the unsatisfiable transitions \YX{may entail some transitions without predecessor} transitions, }
 the set $L1$ might contain unreachable transitions. To remove those transitions, the last step of the  
@@
 
-\subsection{Computing Reachable State Space on the Fly}
+\begin{algorithm}[htbp]
+  \caption{\QINX{makeReachableSubAutomaton()}}
+  \label{alg:makeReachableSubAutomaton}
+\begin{algorithmic}[1]
+\Require \QINX{The initial state of the pNet $\textit{InitState}(P)$. A set of satisfiable transitions $L$.}
+\State Initialize a set $A$;
+\State Store $(\textit{InitState}(P), \textit{InitState}(P).Assignments)$ into $S$;  \hfill $\setminus \setminus$$S.Assignments$ is the assignment of the variable in the state $S$.
+\While{!$\mathit{isEmpty}(A)$}
+	\For {each $(S, Assignments) \in A$}
+          \For {each $OT$ from $S$}
+          \State Check the predicate of $OT$ taking $Assignments$ in to account;
+	  \IfThenElse{$\textit{false}$}{\textbf{skip};}{Add target of $OT$ and its assignments ($S'$, $S'.Assignments$) into $A$;}
+	\EndFor	\EndFor
+\EndWhile
+\State Build $\mathit{OA}$ with the set $L$;
+\State \QINX{\Return $\mathit{OA}$;}
+\end{algorithmic}  
+\end{algorithm}
+
+\begin{algorithm}[htbp]
+  \caption{\QINX{refineReachableSubAutomaton()}}
+  \label{alg:refineReachableSubAutomaton}
+\begin{algorithmic}[1]
+\Require \QINX{An open automaton $\mathit{OA}$.}
+\Repeat
+\For {\QINX{each global state $S$ in $\mathit{OA}$}}
+          \State \QINX{$b=$ whether $S$ has preceeding transitions.}
+	  \IfThenElse{$b$}{\textbf{skip};}{\QINX{remove $S$ and the transitions from $S$;}}
+\EndFor
+\Until  \QINX{$\mathit{OA}$ does not change;}
+\State \QINX{\Return $\mathit{OA}$;}
+\end{algorithmic}  
+\end{algorithm}
+
+\subsection{Computing Reachable State Space on-the-fly}
 
@@
 \State $\mathit{OA_2^0}$=\textit{makeReachableSubAutomaton}($\mathit{InitState}(P),L2)$;
-\Repeat $\mathit{OA_2^n}$=\textit{RefineReachableSubAutomaton}($\mathit{OA_2^{n-1}}$)
+\Repeat $\mathit{OA_2^n}$=\textit{refineReachableSubAutomaton}($\mathit{OA_2^{n-1}}$)
 \Until  $\mathit{OA_2^n}=\mathit{OA_2^{n-1}}$;
@@
 the open automaton needs not to collect the set of possible values dealing
-with the values of local variables, so the final automaton is $AO_2^0$ as
+with the values of local variables, so the final automaton is $OA_2^0$ as
 computed in line 13.

### 2020-01-21 2017-Xudong-SMT/ActaInformatica.tex
Acta paper: More explanation in Sect.4.2 and 4.3.

@@
 range over action constants, $\symb{op}$ over operators, and $x$  over
-variable names. Action terms are given by the following grammar:
+variable names. Action terms (parameterised actions) are given by the following grammar:
 \[
@@
 satisfiability (function \textit{filterUnsatTransitions}). 
-Then we compute (lines 12-14) the set of reachable transitions and states to build
-the final open automaton (more details in Section~\ref{section:BuildingTheOpenAutomaton}).
+\QINX{Then starting at the initial state, we compute (lines 12) the set of reachable transitions and states taking the assignments into account.
+We also iteratively prune (lines 13-14) the unreachable states by refining the possible set of values of states variables (more details in Section~\ref{section:BuildingTheOpenAutomaton}).}
 
@@
 
-In Algorithm~\ref{alg1}, functions \textit{filterUnsatTransitions} (in line 11) 
+In Algorithm~\ref{alg1}, functions \textit{filterUnsatTransitions} (in line 11), 
 \textit{refineReachableSubAutomaton} (in line 13) make use of the Z3 engine to implement the
@@
 for recursive datatypes).
-However, while building the open automaton, which is a symbolic representation of the pNet behaviour, it is not logically incorrect to keep potentially unsatisfiable transitions, so we will treat undecidable results, and time bounds failures, as SAT.
-So the open automaton may have more transitions and states than the theoretical minimum.}
+\QINX{When building the open automaton, which is a symbolic representation of the pNet behaviour, a symbolic transition can be pruned if its predicate is checked unsatisfiable.
+However in some cases SMT finds it undecidable, so we may still have some spurious symbolic transitions in the result.
+We cannot pretend to get minimality, but still it is better to prune as many unsatisfiable transitions as possible, together with some states which become unreachable.
+So we will treat undecidable results, and time bounds failures, as SAT.} So the open automaton may have more transitions and states than the theoretical minimum.}
 
@@
 
-A further reduction may now be gained by using the information from
+\QINX{A further reduction may now be gained by using the information from
 these sets of possible assignments: adding this information when
 checking satisfiability of transitions leaving a given state may
-result in more UNSAT transitions. The set of possible
+result in more UNSAT transitions.
+Furthermore, if there are assignments of state variables inside some loops of the automaton, and the set of their possible values may influence some predicates, we will need more iterations.
+Because in that case more predicates of transitions will be unsatisfiable after pruning some assignments in the previous iteration.} The set of possible
 assignments computed by the algorithm is an over approximation of
@@
 In practice, this could be
-expensive \QIN{as it requires several traversals of the whole set of open transitions}, and it is not incorrect to leave some UNSAT OTs in the
+expensive as it requires several traversals of the whole set of open transitions, and it is not incorrect to leave some UNSAT OTs in the
 result.
-\QIN{\YX{Empirically, on real life systems, the unreachable transitions constitute  a small part of the ultimate} open transitions, very little will be gained to compute the fixed point.
-So we would only perform one step of iteration.} Further algorithms
+Empirically, on real life systems, the unreachable transitions constitute  a small part of the ultimate open transitions, very little will be gained to compute the fixed point.
+So we would only perform one step of iteration.
+Further algorithms
 (e.g. model-checking or equivalence checking) will be able to use the
@@
 
-\begin{algorithm}[htbp]
-  \caption{\QINX{makeReachableSubAutomaton()}}
-  \label{alg:makeReachableSubAutomaton}
-\begin{algorithmic}[1]
-\Require \QINX{The initial state of the pNet $\textit{InitState}(P)$. A set of satisfiable transitions $L$.}
-\State Initialize a set $A$;
-\State Store $(\textit{InitState}(P), \textit{InitState}(P).Assignments)$ into $S$;  \hfill $\setminus \setminus$$S.Assignments$ is the assignment of the variable in the state $S$.
-\While{!$\mathit{isEmpty}(A)$}
-	\For {each $(S, Assignments) \in A$}
-          \For {each $OT$ from $S$}
-          \State Check the predicate of $OT$ taking $Assignments$ in to account;
-	  \IfThenElse{$\textit{false}$}{\textbf{skip};}{Add target of $OT$ and its assignments ($S'$, $S'.Assignments$) into $A$;}
-	\EndFor	\EndFor
-\EndWhile
-\State Build $\mathit{OA}$ with the set $L$;
-\State \QINX{\Return $\mathit{OA}$;}
-\end{algorithmic}  
-\end{algorithm}
-
-\begin{algorithm}[htbp]
-  \caption{\QINX{refineReachableSubAutomaton()}}
-  \label{alg:refineReachableSubAutomaton}
-\begin{algorithmic}[1]
-\Require \QINX{An open automaton $\mathit{OA}$.}
-\Repeat
-\For {\QINX{each global state $S$ in $\mathit{OA}$}}
-          \State \QINX{$b=$ whether $S$ has preceeding transitions.}
-	  \IfThenElse{$b$}{\textbf{skip};}{\QINX{remove $S$ and the transitions from $S$;}}
-\EndFor
-\Until  \QINX{$\mathit{OA}$ does not change;}
-\State \QINX{\Return $\mathit{OA}$;}
-\end{algorithmic}  
-\end{algorithm}
+%\begin{algorithm}[htbp]
+%  \caption{\QINX{makeReachableSubAutomaton()}}
+%  \label{alg:makeReachableSubAutomaton}
+%\begin{algorithmic}[1]
+%\Require \QINX{The initial state of the pNet $\textit{InitState}(P)$. A set of satisfiable transitions $L$.}
+%\State Initialize a set $A$;
+%\State Store $(\textit{InitState}(P), \textit{InitState}(P).Assignments)$ into $S$;  \hfill $\setminus \setminus$$S.Assignments$ is the assignment of the variable in the state $S$.
+%\While{!$\mathit{isEmpty}(A)$}
+%	\For {each $(S, Assignments) \in A$}
+%          \For {each $OT$ from $S$}
+%          \State Check the predicate of $OT$ taking $Assignments$ in to account;
+%	  \IfThenElse{$\textit{false}$}{\textbf{skip};}{Add target of $OT$ and its assignments ($S'$, $S'.Assignments$) into $A$;}
+%	\EndFor	\EndFor
+%\EndWhile
+%\State Build $\mathit{OA}$ with the set $L$;
+%\State \QINX{\Return $\mathit{OA}$;}
+%\end{algorithmic}  
+%\end{algorithm}
+%
+%\begin{algorithm}[htbp]
+%  \caption{\QINX{refineReachableSubAutomaton()}}
+%  \label{alg:refineReachableSubAutomaton}
+%\begin{algorithmic}[1]
+%\Require \QINX{An open automaton $\mathit{OA}$.}
+%\Repeat
+%\For {\QINX{each global state $S$ in $\mathit{OA}$}}
+%          \State \QINX{$b=$ whether $S$ has preceeding transitions.}
+%	  \IfThenElse{$b$}{\textbf{skip};}{\QINX{remove $S$ and the transitions from $S$;}}
+%\EndFor
+%\Until  \QINX{$\mathit{OA}$ does not change;}
+%\State \QINX{\Return $\mathit{OA}$;}
+%\end{algorithmic}  
+%\end{algorithm}
 

### 2020-01-30 2016-Weak-FH-Bisim/WeakBisim.tex
papier au format lmcs
adapt new sty, et remove \TODO pages 12-13

@@
 
-\documentclass[preprint]{elsarticle}
+\documentclass{lmcs}
 
@@
 \newtheorem{theorem}{Theorem}
-\newtheorem{prop}{Proposition}
+%\newtheorem{prop}{Proposition}
 %\newtheorem{corollary}[theorem]{Corollary}
@@
 %\newtheorem{problem}[theorem]{Problem}
-\newenvironment{proof}{\paragraph{Proof}}{}
-
-\title{Compositional equivalences based on Open pNets\thanks{This work was partially 
-funded by the Associated Team FM4CPS
-  between INRIA and ECNU, Shanghai}}
-\author{Ludovic Henrio  \ \ \  Eric Madelaine \ \ \ Rab\'ea}
-%\institute{Univ. of Nice Sophia Antipolis, CNRS, UMR 7271, 06900 Sophia Antipolis, France
-%	\and INRIA Sophia Antipolis M\'edit\'erann\'ee, BP 93, 06902 Sophia Antipolis, France
-%}
-\date{}                                           % Activate to display a given date or no date
-
+%\newenvironment{proof}{\paragraph{Proof}}{}
+
+\begin{document}
+
+\title{Compositional equivalences based on Open pNets
+%\thanks{This work was partially funded by the Associated Team FM4CPS
+%  between INRIA and ECNU, Shanghai}
+}
+\author{Ludovic Henrio}
+
+\author{Eric Madelaine}
+\address{INRIA Sophia Antipolis M\'edit\'erann\'ee, BP 93, 06902 Sophia Antipolis, France}
+%\date{}                                           % Activate to display a given date or no date
+\author{Rab\'ea Ameur-Boulifa}
                           % Activate to display a given date or no date
-
-\begin{document}
-
-\maketitle
 
@@
 \end{abstract}
+
+\maketitle
 
@@
 \paragraph{Previous Works and Contribution}
-While most of our previous works relied on closed, fully-instantiated semantics~\cite{BBCHM:article2008,AmeurBoulifa2017,HKM-FASE16}, it is only recently that we could design a first version of a  parameterised semantics for pNets with a strong bisimulation equivalence~\cite{henrio:Forte2016}.
+While most of our previous works relied on closed, fully-instantiated semantics~\cite{BBCHM:article2008,AmeurBoulifa2017,henrio:hal-01303557}, it is only recently that we could design a first version of a  parameterised semantics for pNets with a strong bisimulation equivalence~\cite{henrio:Forte2016}.
 This article builds open this previous parameterised semantics and provide a cleaner version of the semantics with a slightly simplified formalism and extends it to deal with weak bisimulation.
@@
 
-\LUDO{I added this paragraph}
+%\LUDO{I added this paragraph}
 Because of the semantic interpretation of open automata, the set of open transition of an open automaton is infinite (for example because every free variable can be renamed).
@@
 
-The proof of this theorem can be found in~\ref{thm-equiv-proof}.
-The only non-trivial part of the proof is the proof of transitivity.
-It relies on the following elements.
-First,  the transitive composition of two relations with predicate is defined; this is not exactly standard as it necessitates to define the right predicate for the transitive composition and producing a single predicate to relate any two states.
-Then the fact that one open transition is simulated by a family of open transitions leads to a doubly indexed family of simulating open transition; this needs particular care, also because of the use of renaming (\Post) when proving that the predicates satisfy the definition (property on $\Pred_{s,t} \land \Pred_{OT}$ in the definition).
+The proof of this theorem can be found in~\ref{thm-equiv-proof}. The
+only non-trivial part of the proof is the proof of transitivity. It
+relies on the following elements. First,  the transitive composition
+of two relations with predicate is defined; this is not exactly
+standard as it necessitates to define the right predicate for the
+transitive composition and producing a single predicate to relate any
+two states. Then the fact that one open transition is simulated by a
+family of open transitions leads to a doubly indexed family of
+simulating open transition; this needs particular care, also because
+of the use of renaming (\Post) when proving that the predicates
+satisfy the definition (property on $\Pred_{s,t} \land \Pred_{OT}$ in
+the definition).
 
@@
 
-\TODO{J'ai un probleme ici, comme on a dit que les AO etaient satures par substitution, ils sont par nature infinis...
+%\TODO{J'ai un probleme ici, comme on a dit que les AO etaient satures par substitution, ils sont par nature infinis...
 Donc le theoreme, tel qu'il est exprime, est vrai, mais inapplicable.
 La solution est dans le papier de PEPM, mais complique a expliquer...}
-\TODO{pour faire simple, on vire le theoreme, et on met une simple note disant qu'on a une definition dans PEPM d'une description structurelle finie, et un algo avec terminaison ?}
-\TODO{[LUDO->ERIC] D'accord: tu ecris comme tu connais le mieux le papier PEPM?}
+%\TODO{pour faire simple, on vire le theoreme, et on met une simple note disant qu'on a une definition dans PEPM d'une description structurelle finie, et un algo avec terminaison ?}
+%\TODO{[LUDO->ERIC] D'accord: tu ecris comme tu connais le mieux le papier PEPM?}
+
+\paragraph{Note on finite versus infinite open automata:} as
+mentionned in page \pageref{def:open-automaton}, we have defined two flavors of
+automata. More precisely, in \cite{hou:hal-02406098}, we formely define
+\emph{semantic open automata} (infinite as in Definition \ref{def:open-automaton}),
+and \emph{structural open automata} (finite) that can be generated as
+the semantics of pNets, and used in the implementation. Then we define
+an alternative version of our bisimulation, called
+Structural-FH-Bisimulation, based on structural open automata, and
+prove that the \emph{semantic} and \emph{structural} FH-Bisimulations coincide.
+In the sequel, all mentions of finite automata, and algorithms for
+bisimulations, implicitely refer to their \emph{structural} versions.
+
 If we assume that everything is finite (states and transitions in the
@@
 prove that it is decidable whether a relation is a 
-FH-bisimulation, provided the logic of the predicates is decidable (see \cite{henrio:Forte2016}).
+FH-bisimulation, provided the logic of the predicates is
+decidable (see \cite{henrio:Forte2016}). Formaly:
 
@@
 This section defines the semantics of an open pNet as a translation into an open automaton. 
-In this translation, the states of the open automata are obtained from the states of the pLTSs at the leaves of the composition.
-The predicates on the transitions are obtained both from the predicates on the pLTSs transitions and from the synchronisation vectors involved in the transition.
-\TODO{Meme remarque ici, on ne genere qu'une representation finie des OAs}
-
-The definition of bisimulation for open automata allows us to derive a bismulation theory for open pNets.
-As pNets are composition structures, it then makes sense to prove composition lemmas: we prove that the composition of strongly bisimilar pNets are themselves bisimilar.
+In this translation, the states of the open automata are obtained from
+the states of the pLTSs at the leaves of the composition. The
+predicates on the transitions are obtained both from the predicates on
+the pLTSs transitions and from the synchronisation vectors involved in
+the transition.
+
+The definition of bisimulation for open automata allows us to derive a
+bismulation theory for open pNets. As pNets are composition
+structures, it then makes sense to prove composition lemmas: we prove
+that the composition of strongly bisimilar pNets are themselves
+bisimilar.
 

### 2020-01-31 2016-Weak-FH-Bisim/WeakBisim.tex
note page 12

@@
 
-%\TODO{J'ai un probleme ici, comme on a dit que les AO etaient satures par substitution, ils sont par nature infinis...
-Donc le theoreme, tel qu'il est exprime, est vrai, mais inapplicable.
-La solution est dans le papier de PEPM, mais complique a expliquer...}
-%\TODO{pour faire simple, on vire le theoreme, et on met une simple note disant qu'on a une definition dans PEPM d'une description structurelle finie, et un algo avec terminaison ?}
-%\TODO{[LUDO->ERIC] D'accord: tu ecris comme tu connais le mieux le papier PEPM?}
+\TODO{[LUDO->ERIC] D'accord: tu ecris comme tu connais le mieux le
+  papier PEPM?}
+\TODO{Ludo, tu peux relire, stp ?}
 
@@
 and \emph{structural open automata} (finite) that can be generated as
-the semantics of pNets, and used in the implementation. Then we define
+the semantics of pNets (see Def. \ref{def:operationalSemantics}), and used in the implementation. Then we define
 an alternative version of our bisimulation, called
-Structural-FH-Bisimulation, based on structural open automata, and
+structural-FH-Bisimulation, based on structural open automata, and
 prove that the \emph{semantic} and \emph{structural} FH-Bisimulations coincide.

### 2020-01-31 2016-Weak-FH-Bisim/WeakBisim.tex
note page 12 (re)

@@
 and \emph{structural open automata} (finite) that can be generated as
-the semantics of pNets (see Def. \ref{def:operationalSemantics}), and used in the implementation. Then we define
+the semantics of pNets (see Definition \ref{def:operationalSemantics}), and used in the implementation. Then we define
 an alternative version of our bisimulation, called
@@
 FH-bisimulation, provided the logic of the predicates is
-decidable (see \cite{henrio:Forte2016}). Formaly:
+decidable (proof in \cite{henrio:Forte2016}). Formaly:
 

### 2020-02-03 2016-Weak-FH-Bisim/WeakBisim.tex
english in finite+decidability

@@
 
-\TODO{[LUDO->ERIC] D'accord: tu ecris comme tu connais le mieux le
-  papier PEPM?}
-\TODO{Ludo, tu peux relire, stp ?}
-
-\paragraph{Note on finite versus infinite open automata:} as
+\subsubsection*{Note on finite versus infinite open automata:} as
 mentionned in page \pageref{def:open-automaton}, we have defined two flavors of
@@
 In the sequel, all mentions of finite automata, and algorithms for
-bisimulations, implicitely refer to their \emph{structural} versions.
+bisimulations, implicitly refer to their \emph{structural} versions.
 
@@
 FH-bisimulation, provided the logic of the predicates is
-decidable (proof in \cite{henrio:Forte2016}). Formaly:
+decidable (proof in \cite{henrio:Forte2016}). Formally:
 

### 2020-02-04 2016-Weak-FH-Bisim/WeakBisim.tex
new proposal page 22

@@
 
-$$ 1 = \openrule
-         {\{P\mapsto\texttt{p-a}\}, [\forall m.p-a!=P\_send(m)], () }
-         {000 \OTWeakarrow {\texttt{p-a}} 000}$$
+Here I denote as $post_n$ the effect of the Strong transition $OT_n$ from Figure \ref{}:
+$$post_3 = (s1\_c\gets 0, s1\_m\gets m)$$
+$$post_4 = (m1\_msg\gets s1\_msg, m1\_c\gets s1\_c)$$
+$$post_5 = (m2\_c\gets m1\_c)$$
+$$post_6 = (s1\_c\gets m2\_c+1)$$
+
+Then the effect of one single $100 -> 210 -> 220 -> 100$ loop as:
+$$Post_{456} = post_6\shortotimes post_5\shortotimes post_4$$
+
+And $WOT_4$ becomes:
+$$ 3 = \openrule
+         {\{P\mapsto\texttt{p\_send(m)}\}, True, post_4\shortotimes {Post_{456}}^*\shortotimes\ post_3}
+         {000 \OTWeakarrow {\texttt{in(m)}} 100}$$
 \\
-$$6 = \openrule
-         {\{\}, [True], () }
-         {100 \OTWeakarrow {\tau\big(\subst{m1\_c:=s1\_c,m1\_m:=s1\_m,s2\_c:=s1\_c}\subst{s1\_c:=s2\_c+1}\big)^* \subst{m1\_c:=s1\_c,m1\_m:=s1\_m,s2\_c:=s1\_c} } 210}
+$$4 = \openrule
+         {\{\}, True, post_4\shortotimes {Post_{456}}^* }
+         {100 \OTWeakarrow {\tau} 210}
          $$

### 2020-02-04 2016-Weak-FH-Bisim/WeakBisim.tex

--- 2020-02-03 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
-\TODO{Eric: insert here a table with the details of the WOTs...}
+\TODO{Eric: insert here a table with the details of the WOTs.Il manque encore au moins 3 WOT dans ce dessin...}
 
@@
 $2^nd$ try, full formal style ?:
-
-$$ 1 = \openrule
-         {\{P\mapsto\texttt{p-a}\}, [\forall m.p-a!=P\_send(m)], () }
-         {000 \OTWeakarrow {\texttt{p-a}} 000}$$
-\\
-$$6 = \openrule
-         {\{\}, [True], () }
-         {100 \OTWeakarrow {\tau\big(\subst{m1\_c:=s1\_c,m1\_m:=s1\_m,s2\_c:=s1\_c}\subst{s1\_c:=s2\_c+1}\big)^* \subst{m1\_c:=s1\_c,m1\_m:=s1\_m,s2\_c:=s1\_c} } 210}
-         $$
+\medskip
+
+Here we denote as $post_n$ the effect of the Strong transition $OT_n$ from Figure \ref{}:
+\smallskip
+
+$post_1 = post_2 = ()$
+
+$post_3 = (s1\_c\gets 0, s1\_m\gets m)$
+
+$post_4 = (m1\_msg\gets s1\_msg, m1\_c\gets s1\_c)$
+
+$post_5 = (m2\_c\gets m1\_c)$
+
+$post_6 = (s1\_c\gets m2\_c+1)$
+
+$post_7 = (r1\_msg\gets m1\_msg, r1\_c\gets m1\_c)$
+
+$post_8 = ()$
+\medskip
+
+Then the effect of one single $100 -> 210 -> 220 -> 100$ loop as:
+\smallskip
+
+$Post_{456} = post_6\shortotimes post_5\shortotimes post_4$
+\medskip
+
+And we can now define the weak OTs:
+\smallskip
+
+$ 1 = \openrule
+{\{P\mapsto p\_a\}, [\forall m. p\_a \neq p\_send(m)], ()}
+{000 \OTWeakarrow {\tau} 000}
+$
+
+$ 3 = \openrule
+         {\{P\mapsto p\_send(m)\}, True, post_4\shortotimes {Post_{456}}^*\shortotimes\ post_3}
+         {000 \OTWeakarrow {\texttt{in(m)}} 100}$
+
+$ 4 = \openrule
+         {\{\}, True, post_4\shortotimes {Post_{456}}^* }
+         {100 \OTWeakarrow {\tau} 210}
+         $
+
+$ 5 = \openrule
+         {\{\}, True, {Post_{564}}^* }
+         {210 \OTWeakarrow {\tau} 220}
+         $
+
+$ 6 = \openrule
+         {\{\}, True, {Post_{456}}^*\shortotimes post_6 }
+         {220 \OTWeakarrow {\tau} 100}
+         $
+
+$ 7 = \openrule
+         {\{\}, True, post_7\shortotimes {Post_{564}}^* }
+         {220 \OTWeakarrow {\tau} 100}
+         $
 

### 2020-02-04 2016-Weak-FH-Bisim/WeakBisim.tex
nearly finished Fig 7
+1

@@
 
-\TODO{Eric: insert here a table with the details of the WOTs.Il manque encore au moins 3 WOT dans ce dessin...}
-
-\smallskip
-$1^st$ try, user-friendly style:
-
-$$ 3 = \tau^*; \underline{in(m)}\{s1\_c:=0, s1\_m:=m\}; \tau\{s1\_c++\}^*$$
-
-\smallskip
-$2^nd$ try, full formal style ?:
-\medskip
+\TODO{Define $\tau = \openrule{\{\}, True, ()}{xxx \OTWeakarrow {\tau} xxx}$}
+
+\TODO{Define *}
+
+% \TODO{Eric: insert here a table with the details of the WOTs.Il manque encore au moins 3 WOT dans ce dessin...}
+
+% \smallskip
+% $1^st$ try, user-friendly style:
+
+% $$ 3 = \tau^*; \underline{in(m)}\{s1\_c:=0, s1\_m:=m\}; \tau\{s1\_c++\}^*$$
+
+%\smallskip
+%$2^nd$ try, full formal style ?:
+%\medskip
 
@@
 
-Then the effect of one single $100 -> 210 -> 220 -> 100$ loop as:
+Then the effect of one single $100 \rightarrow{4} 210 \rightarrow{5} 220 \rightarrow{6} 100$ loop as:
 \smallskip
 
-$Post_{456} = post_6\shortotimes post_5\shortotimes post_4$
+$Post_{456} = post_6\shortotimes post_5\shortotimes post_4$, that can be simplified as: $(s1\_c\gets s1\_c+1)$
 \medskip
 
-And we can now define the weak OTs:
+Iterating as: ${Post_{456}}^*$ =  $(s1\_c\gets s1\_c+n)$ for some $n\ge 0$
+\medskip
+
+Finaly WOT 3 has a substitution $\shortotimes {Post_{456}}^*\shortotimes\ post_3$ = $(s1\_c\gets 0+n)$
+\medskip
+
+and WOT 3' has $post_4\shortotimes {Post_{456}}^*\shortotimes\ post_3$
+= $(m1\_msg\gets m, m1\_c\gets 0+n)$
+\medskip
+
+We can now define the weak OTs:
 \smallskip
@@
 $ 3 = \openrule
+         {\{P\mapsto p\_send(m)\}, True, {Post_{456}}^*\shortotimes\ post_3}
+         {000 \OTWeakarrow {\texttt{in(m)}} 100}$
+
+$ 3' = \openrule
          {\{P\mapsto p\_send(m)\}, True, post_4\shortotimes {Post_{456}}^*\shortotimes\ post_3}
-         {000 \OTWeakarrow {\texttt{in(m)}} 100}$
+         {000 \OTWeakarrow {\texttt{in(m)}} 210}$
 

### 2020-02-05 2016-Weak-FH-Bisim/WeakBisim.tex
figure SPImplOpen
ajout figure SPSpecWeakOpen

--- 2020-02-04 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
+%\begin{figure}[ht]
+%   \centerline{\includegraphics[width=11cm]{ATG/SPSpecOpen}}
+%   \caption{Specification OA}
+%   \label{SimpleProtCounter:SpecOA}
+%\end{figure}
+
 \begin{figure}[ht]
-   \centerline{\includegraphics[width=11cm]{ATG/SPSpecOpen}}
-   \caption{Specification OA}
-   \label{SimpleProtCounter:SpecOA}
-\end{figure}
-
-\begin{figure}[ht]
-   \centerline{\includegraphics[width=10cm]{XFIG/SPSpecOpen}}
+   \centerline{\includegraphics[width=9cm]{XFIG/SPSpecOpen}}
    \caption{Specification OA}
@@
     \begin{figure}[ht]
-  \centerline{\includegraphics[width=10cm]{ATG/SPImplOpen}}
+  %\centerline{\includegraphics[width=10cm]{ATG/SPImplOpen}}
   \caption{Open Automaton of the Simple Protocol Implementation}  \label{SimpleProtCounter:ImplOA}
@@
  WOT2 here is the transition delivering the result of the algorithm to hole $Q$.
-Remark that it includes a loop increasing the error counter, occuring before the action of $Q$, and this action is using the resulting value of the counter.
+Remark that it includes a loop increasing the error counter, occurring before the action of $Q$, and this action is using the resulting value of the counter.
 Let us go into the details, using rules WT1/2/3.
@@
 \begin{figure}[h]
-   \centerline{\includegraphics[width=10cm]{ATG/SPSpecWeakOpen}}
+   \centerline{\includegraphics[width=15cm]{ATG/SPSpecWeakOpen}}
   \caption{Weak Open Automaton of the Specification \TODO{out of date}}
+   \label{SimpleProtCounter:WeakSpecOA}
+\end{figure}
+
+\begin{figure}[h]
+   \centerline{\includegraphics[width=10cm]{XFIG/SPSpecWeakOpen}}
+  \caption{Weak Open Automaton of the Specification}
    \label{SimpleProtCounter:WeakSpecOA}

### 2020-02-05 2016-Weak-FH-Bisim/WeakBisim.tex
remove *pdf from the repo
full WOT in page 22

@@
   %\centerline{\includegraphics[width=10cm]{ATG/SPImplOpen}}
-  \caption{Open Automaton of the Simple Protocol Implementation}  \label{SimpleProtCounter:ImplOA}
+  \caption{Open Automaton of the Simple Protocol Implementation}  %\label{SimpleProtCounter:ImplOA}
 \end{figure}
@@
 Rule WT2 transforms each 3 OTs into WOTs.
-In the drawing we use \texttt{ec++} to abbreviate the Post: $\subst{ec\gets ec+1}$.
 Then WT3 produces the weak OT:
@@
 
-         For any of these, apply again WT3, using the central \texttt{q-recv(ec)} transition as $\alpha$, and you get:
+         For any of these, apply again WT3, using the central \texttt{q\_recv(ec)} transition as $\alpha$, and you get:
       $\openrule
-         {\{Q\mapsto\texttt{q-revc(ec)}\subst{ec\gets ec+n}\}, True,
+         {\{Q\mapsto\texttt{q\_revc(ec)}\subst{ec\gets ec+n}\}, True,
 			\subst{ec\gets ec+n} }
@@
 \begin{figure}[h]
-   \centerline{\includegraphics[width=15cm]{ATG/SPSpecWeakOpen}}
+   \centerline{\includegraphics[width=13cm]{ATG/SPSpecWeakOpen}}
   \caption{Weak Open Automaton of the Specification \TODO{out of date}}
@@
 \begin{figure}[h]
-   \centerline{\includegraphics[width=10cm]{XFIG/SPSpecWeakOpen}}
+   \centerline{\includegraphics[width=12cm]{XFIG/SPSpecWeakOpen}}
   \caption{Weak Open Automaton of the Specification}
@@
 
-\TODO{Eric: insert here a table with the details of the WOTs.Il manque encore au moins 3 WOT dans ce dessin...}
-
+%% \TODO{Eric: insert here a table with the details of the WOTs.Il manque encore au moins 3 WOT dans ce dessin...}
+
+%% \smallskip
+%% $1^st$ try, user-friendly style:
+
+%% $$ 3 = \tau^*; \underline{in(m)}\{s1\_c:=0, s1\_m:=m\}; \tau\{s1\_c++\}^*$$
+
+%% \smallskip
+%% $2^nd$ try, full formal style ?:
+%% \medskip
+
+Now let us give some details about the construction of the weak automation of the implementation pNet, obtained by application of the weak rules as explained above.
+Here we denote as $post_n$ the effect (= susbtitution) of the Strong transition $OT_n$ from Figure \ref{SimpleProtCounter:ImplOA}:
 \smallskip
-$1^st$ try, user-friendly style:
-
-$$ 3 = \tau^*; \underline{in(m)}\{s1\_c:=0, s1\_m:=m\}; \tau\{s1\_c++\}^*$$
-
+
+$post_1 = post_2 = ()$
+
+$post_3 = (\texttt{s1\_c}\gets 0, \texttt{s1\_m}\gets \texttt{m})$
+
+$post_4 = (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_c}\gets \texttt{s1\_c})$
+
+$post_5 = (\texttt{m2\_c}\gets \texttt{m1\_c})$
+
+$post_6 = (\texttt{s1\_c}\gets \texttt{m2\_c+1})$
+
+$post_7 = (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_c}\gets \texttt{m1\_c})$
+
+$post_8 = post_9 = ()$
+\medskip
+
+Then the effect of one single $100 \xrightarrow{OT_4} 210 \xrightarrow{OT_5} 220 \xrightarrow{OT_6} 100$ loop is:
 \smallskip
-$2^nd$ try, full formal style ?:
+
+$Post_{456} = post_6 \shortotimes\ post_5 \shortotimes\ post_4
+= (s1\_c\gets s1\_c+1)$.
 \medskip
 
-Here we denote as $post_n$ the effect of the Strong transition $OT_n$ from Figure \ref{}:
+So if we denote ${Post_{456}}^*$ any iteration of this loop, we get ${Post_{456}}^* = (\texttt{s1\_c}\gets \texttt{s1\_c}+n)$ for any $n\ge 0$, and we will get e.g.
+the Post of the weak OT number 3' as $ post_4\shortotimes {Post_{456}}^*\shortotimes\ post_3 = (\texttt{m1\_msg}\gets m, \texttt{m1\_c}\gets n), \forall n\ge 0$
+\medskip
+
+We can now show some of the weak OTs of Figure \ref{SimpleProtCounter:SpecOA-partial} (the full table will be included in Appendix \ref{Appendix:FullExample}) :
 \smallskip
 
-$post_1 = post_2 = ()$
-
-$post_3 = (s1\_c\gets 0, s1\_m\gets m)$
-
-$post_4 = (m1\_msg\gets s1\_msg, m1\_c\gets s1\_c)$
-
-$post_5 = (m2\_c\gets m1\_c)$
-
-$post_6 = (s1\_c\gets m2\_c+1)$
-
-$post_7 = (r1\_msg\gets m1\_msg, r1\_c\gets m1\_c)$
-
-$post_8 = ()$
-\medskip
-
-Then the effect of one single $100 -> 210 -> 220 -> 100$ loop as:
-\smallskip
-
-$Post_{456} = post_6\shortotimes post_5\shortotimes post_4$
-\medskip
-
-And we can now define the weak OTs:
-\smallskip
-
 $ 1 = \openrule
-{\{P\mapsto p\_a\}, [\forall m. p\_a \neq p\_send(m)], ()}
-{000 \OTWeakarrow {\tau} 000}
-$
+{\{\texttt{P}\mapsto \texttt{p\_a}\}, [\forall \texttt{m}. \texttt{p\_a} \neq \texttt{p\_send(m)} ], ()}
+{000 \OTWeakarrow {\tau} 000}$
+
+$ 2 = \openrule
+{\{\texttt{Q}\mapsto \texttt{q\_b}\}, [\forall \texttt{m}. \texttt{q\_b} \neq \texttt{q\_recv(m)} ], ()}
+{000 \OTWeakarrow {\tau} 000}$
 
 $ 3 = \openrule
-         {\{P\mapsto p\_send(m)\}, True, post_4\shortotimes {Post_{456}}^*\shortotimes\ post_3}
-         {000 \OTWeakarrow {\texttt{in(m)}} 100}$
+  {\{\texttt{P}\mapsto \texttt{p\_send(m)}\}, True,
+    (\texttt{s1\_msg}\gets m, \texttt{s1\_c}\gets n)}
+  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
+  \forall n\ge 0$
+
+$ 3' = \openrule
+  {\{\texttt{P}\mapsto \texttt{p\_send(m)}\}, True,
+    (\texttt{m1\_msg}\gets m, \texttt{m1\_c}\gets n)}
+  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 210}
+  \forall n\ge 0$
+
+$ 3'' = \openrule
+  {\{\texttt{P}\mapsto \texttt{p\_send(m)}\}, True, 
+    (\texttt{m2\_c}\gets n)}
+  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 220}
+  \forall n\ge 0$
 
          $ 4 = \openrule
-         {\{\}, True, post_4\shortotimes {Post_{456}}^* }
+         {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_c}\gets \texttt{s1\_c}+n)}
          {100 \OTWeakarrow {\tau} 210}
-         $
+         \forall n\ge 0$
 
 $ 5 = \openrule
-         {\{\}, True, {Post_{564}}^* }
+         {\{\}, True, (\texttt{m2\_c}\gets \texttt{m1\_c}+n)}
          {210 \OTWeakarrow {\tau} 220}
-         $
+         \forall n\ge 0$
 
 $ 6 = \openrule
-         {\{\}, True, {Post_{456}}^*\shortotimes post_6 }
+         {\{\}, True, (\texttt{s1\_c}\gets \texttt{m2\_c}+n)}
          {220 \OTWeakarrow {\tau} 100}
-         $
+         \forall n\ge 0$
 
 $ 7 = \openrule
-         {\{\}, True, post_7\shortotimes {Post_{564}}^* }
-         {220 \OTWeakarrow {\tau} 100}
+         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_c}\gets \texttt{s1\_c}+n)}
+         {100 \OTWeakarrow {\tau} 201}
+         \forall n\ge 0$
+
+$ 7' = \openrule
+         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_c}\gets \texttt{m1\_c}+n)}
+         {210 \OTWeakarrow {\tau} 201}
+         \forall n\ge 0$
+
+$ 7'' = \openrule
+         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_c}\gets \texttt{m2\_c}+n)}
+         {220 \OTWeakarrow {\tau} 201}
+         \forall n\ge 1$
+
+$ 8 = \openrule
+         {\{\}, True, ()}
+         {201 \OTWeakarrow {\underline{\texttt{out(m,c)}}\subst{(m\gets \texttt{r1\_msg}, c\gets \texttt{r1\_c}}} 202}
          $
@@
 
+\label{Appendix:FullExample}
+
 %% \begin{figure}[t]
@@
 The first piece of code is the textual definition of the SimpleProtSec
-pNet, that was drwan in Figure \ref{SimpleProt:Impl}, page \pageref{SimpleProt:Impl}. This code should be intuitive enough to read, with the following
+pNet, that was drawn in Figure \ref{SimpleProt:Impl}, page \pageref{SimpleProt:Impl}. This code should be intuitive enough to read, with the following
 conventions, that brings some user-friendly features that are maps by the editor into pure pNet constructs.

### 2020-02-05 2016-Weak-FH-Bisim/WeakBisim.tex
details in 5.7

@@
 \begin{figure}[h]
-   \centerline{\includegraphics[width=12cm]{XFIG/SPSpecWeakOpen}}
+   \centerline{\includegraphics[width=15cm]{XFIG/SPSpecWeakOpen}}
   \caption{Weak Open Automaton of the Specification}
@@
 
-Now let us give some details about the construction of the weak automation of the implementation pNet, obtained by application of the weak rules as explained above.
-Here we denote as $post_n$ the effect (= susbtitution) of the Strong transition $OT_n$ from Figure \ref{SimpleProtCounter:ImplOA}:
+Now let us give some details about the construction of the weak automaton of the implementation pNet, obtained by application of the weak rules as explained above.
+Here we denote as $post_n$ the effect (= substitution) of the strong open transition $OT_n$ from Figure \ref{SimpleProtCounter:ImplOA}:
 \smallskip
@@
 $Post_{456} = post_6 \shortotimes\ post_5 \shortotimes\ post_4
-= (s1\_c\gets s1\_c+1)$.
+= (\texttt{s1\_c}\gets \texttt{s1\_c}+1)$.
 \medskip
@@
   {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
-  \forall n\ge 0$
+  \ \forall n\ge 0$
 
@@
   {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 210}
-  \forall n\ge 0$
+  \ \forall n\ge 0$
 
@@
   {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 220}
-  \forall n\ge 0$
+  \ \forall n\ge 0$
 
@@
          {100 \OTWeakarrow {\tau} 210}
-         \forall n\ge 0$
+         \ \forall n\ge 0$
 
@@
          {210 \OTWeakarrow {\tau} 220}
-         \forall n\ge 0$
+         \ \forall n\ge 0$
 
@@
          {220 \OTWeakarrow {\tau} 100}
-         \forall n\ge 0$
+         \ \forall n\ge 0$
 
@@
          {100 \OTWeakarrow {\tau} 201}
-         \forall n\ge 0$
+         \ \forall n\ge 0$
 
@@
          {210 \OTWeakarrow {\tau} 201}
-         \forall n\ge 0$
+         \ \forall n\ge 0$
 
@@
          {220 \OTWeakarrow {\tau} 201}
-         \forall n\ge 1$
+         \ \forall n\ge 1$
 
@@
 
-Beforedefining a weak open automaton for the semantics of open pNets, it is necessary to state under which condition a pNet is unable to observe silent actions of its holes.
-In the setting of pNets this can simply be expressed as a condition on the synchronisation vectors.
-Precisely, the set of synchronisation vectors must contain vectors that let silent actions go through the pNet, i.e.
-synchronisation vectors where one hole does a $\tau$ transition, and the global visible action is a $\tau$.
-Additionally, no other synchronisation vector must be able to react on a silent action from a hole, i.e.
-if a synchronisation vector observes a $\tau$ from a hole it cannot synchronise it with another action nor emit an action that is not $\tau$.
-This is formalised as follows
+Before defining a weak open automaton for the semantics of open pNets,
+it is necessary to state under which condition a pNet is unable to
+observe silent actions of its holes. In the setting of pNets this can
+simply be expressed as a condition on the synchronisation
+vectors. Precisely, the set of synchronisation vectors must contain
+vectors that let silent actions go through the pNet,
+i.e. synchronisation vectors where one hole does a $\tau$ transition,
+and the global visible action is a $\tau$. Additionally, no other
+synchronisation vector must be able to react on a silent action from a
+hole, i.e. if a synchronisation vector observes a $\tau$ from a hole
+it cannot synchronise it with another action nor emit an action that
+is not $\tau$. This is formalised as follows:
 
@@
 \subsection{Running example}
-- In section \ref{} we have shown the full satured weak automaton for both the specification and the implementation of the simple protocol.
+- In section \ref{def:weakOT} we have shown the full satured weak automaton for both the specification and the implementation of the simple protocol.
 
@@
 
-  \TODO{Eric: this is still ABP ! rewrite completely, baesd on saturation example 2 pages before.}
-
-The ``saturation'' step in the construction of the weak relation will
-pick all $\tau^*$ and $\tau^*;a;\tau^*$ sequences from the OA, and build a weak
-open transition from each sequence. Here is one example of a short sequence,
-starting with the open transition $OT_1$ of page \pageref{OT:SimpleProt},
-then transmitting the message to the receiver, and to the environment. The two
-firsts open transitionTs are internal, the last one is visible, so it constitute a
-$\tau;\tau;a$ weak transition.
-
-noindent
-     $  \openrule{
-      \emptyset; Pred=\True; Post=\{m_1\_m:=s_1\_m, m_1\_b:=s_1\_sb, s_2\_sb:=s_1\_sb\}
-                      }
-    {\ostate{s_1,m_0,m_0,r_0} \OTarrow{\underline{send(s_1\_m, s_1\_b)}} \ostate{s_2,m_1,m_0,r_0}}
-    $
-
-\medskip\noindent
-     $  \openrule{
-      \emptyset; Pred=[r_0\_rb=?b' \land ?m'=m_1\_m \land ?b=m_1\_b \land SV3\_m=?m' \land SV3\_b=?b'];
-      \\ Post=\{r_1\_rb:=r_0\_rb; r_1\_m:=?m'; r_1\_b:=?b'      \}
-                      }
-    {\ostate{s_2,m_1,m_0,r_0} \OTarrow{\underline{recv(SV3\_m, SV3\_b)}} \ostate{s_2,m_0,m_0,r_1}}
-    $
-
-    \ERIC{Apres simplification:}
-
-\medskip\noindent
-     $  \openrule{
-      \emptyset; Pred=[r_0\_rb=m_1\_b];
-      \\ Post=\{r_1\_rb:=r_0\_rb; r_1\_m:=m_1\_m; r_1\_b:=m_1\_b      \}
-                      }
-    {\ostate{s_2,m_1,m_0,r_0} \OTarrow{\underline{recv(m_1\_m,m_1\_b)}} \ostate{s_2,m_0,m_0,r_1}}
-    $
-    \\
-
-\medskip\noindent
-     $  \openrule{
-  \emptyset; Pred=\True; Post=r_2\_b:=r_1\_b; s_2\_b:=s_1\_b   \}
-                      }
-    {\ostate{s_2,m_0,m_0,r_1} \OTarrow{out(r_1\_m)} \ostate{s_2,m_0,m_0,r_2}}
-    $
-    \\
-
-    \bigskip
-    ...
-    \bigskip
-
-The resulting Weak Transition has a predicate $\phi =
-\phi_1\land\phi_2\psi_1\land\phi_3\psi_2\psi_1 = \phi=[x=s_1\_b \land m=s_1\_m
-  \land r_0\_b=b \land m'=m_1\_m \land b=m_1\_x
-  \land v=out(r_1\_m)]$
-and assignment
-$\psi= \{r_2\_b:=r_0\_b\}$.
-
-We can see here that in $\phi$ the application of assignments
-$\psi_1,\psi_2,\psi_3$ have already ``eliminated'' the intermediate
-state variables
-$m_1\_m, b=m_1\_x, r_1\_m$, and not the intermediate input variables
-$m,m',x,b$. But now $\phi$ includes enough information to eliminate them, giving
-a final $\phi'= [v=out(s_1\_m)\land r_0\_b=s_1\_b]$, so the resulting
-WOT is:
-
- \noindent
- $$ \openrule{
-   \emptyset; Pred=[r_0\_b=s_1\_b]; Post= \{r_2\_b:=r_0\_b  \}
-   }
-   {\ostate{s_1,m_0,m_0,r_0}\OTWeakarrow{out(s_1\_m)} \ostate{s_2,m_0,m_0,r_2}}$$
-%% \\
-%% $\phi=[x=s_1\_b \land m=s_1\_m\\
-%%   \land r_0\_b=b \land m'=m_1\_m \land b=m_1\_x\\
-%%   \land v=out(r_1\_m)]\\
-%% and \\
-%% \psi= \{r_2\_b:=r_0\_b\}$
-
-%% Note that
+  \begin{itemize}
+    \item[] Both pNets trivialy verify the ``non-observability''
+      condition: the only vectors having $\tau$ as an action of a
+      sub-net are of the form ``$< -, \tau, -> -> \tau$''.
+  \end{itemize}
+
+  Now consider the following triples:
 

### 2020-02-10 2016-Weak-FH-Bisim/WeakBisim.tex
comments figures

@@
 argument, through the two protocol entities.
-Process $P$ send an $p\_send(m)$ message to the $Sender$; this communication is denoted as $\underline{in(m)}$, where underline actions represent internal actions (similar to the $\tau$ of CCS), that cannot be further synchronised with the environment.
+Process $P$ send an $\texttt{p\_send(m)}$ message to the $Sender$; this communication is denoted as $\texttt{\underline{in(m)}}$, where underline actions represent internal actions (similar to the $\tau$ of CCS), that cannot be further synchronised with the environment.
 At the other end process $Q$ receives the message from the $Receiver$.
-The holes $P$ and $Q$ can also have other interactions with their environment, represented here by actions $p\_a$ and $q\_b$.
+The holes $P$ and $Q$ can also have other interactions with their environment, represented here by actions $\texttt{p\_a}$ and $\texttt{q\_b}$.
 The underlying network is modelled by a medium entity transporting messages from the sender to the receiver, and that is able to detect transport errors, and signal them to the sender.
@@
 Nodes of the tree are synchronized using four synchronization vectors, that  express the possible synchronization between the parameterized actions of a subset of the nodes.
-For instance, in the vector "$< p\_send(m),in(m),\_> \rightarrow \underline{in(m)}$ only $P$ and {\it PrefectBuffer} nodes are involved in the synchronization.
-More precisely, the synchronization between these processes occurs when  process $P$  performs $p\_send(m)$  action sending a message, and  the medium accepts the message through $in(m)$ action  at the same time.
-And the result that will be returned at upper level is the internal action  $\underline{in(m)}$.
+For instance, in the vector "$< \texttt{p\_send(m)},\texttt{in(m)},\_> \rightarrow \texttt{\underline{in(m)}}$ only $P$ and {\it PrefectBuffer} nodes are involved in the synchronization.
+More precisely, the synchronization between these processes occurs when  process $P$  performs $p\_send(m)$  action sending a message, and  the medium accepts the message through $\texttt{\texttt{in(m)}}$ action  at the same time.
+And the result that will be returned at upper level is the internal action  $\texttt{\underline{in(m)}}$.
 
@@
 \ref{SimpleProt:Impl} shows the pNet model of the protocol implementation.
-When the $Medium$ detects an error (modeled by a local $\tau$ action), it sends back a $m\_error$ message to the $Sender$.
+When the $Medium$ detects an error (modeled by a local $\tau$ action), it sends back a $\texttt{m\_error}$ message to the $Sender$.
 The $Sender$ increments its local error counter $ec$, and resends the message (including $ec$) to the $Medium$, that will, eventually, transmit $m,ec$ to the $Receiver$.
@@
 \begin{figure}[ht]
-   \centerline{\includegraphics[width=9cm]{XFIG/SPSpecOpen}}
+   \centerline{\includegraphics[width=12cm]{XFIG/SPSpecOpen}}
    \caption{Specification OA}
@@
 
-\paragraph{Example} Figure \ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the Specification pNet in Figure \ref{SimpleProt:Spec}. 
-\RAB{Here, in the open automaton drawing, we use a user-friendly notation for the OTs, in the form ``$\{actions of holes\} [guard] action \{assigns\}$'', rather than the full OT form with the red-dotted rule.
-Note that the resulting action of the OTs appear here between the guard and the set of assignments.
-For example in the upper left of the figure, the OT where $\beta=\{P\mapsto p\_a\}$, $\Pred=[\forall m.
-P\_a\neq p\_send(m)]$, and $\alpha=P\_a$ is denoted as ``\texttt{\{P->p-a\} [Forall m.P-a!=p-send(m)] P-a}''.
-}
+\paragraph{Example} Figure \ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the Specification pNet given in Figure \ref{SimpleProt:Spec}.
+
+%    \begin{figure}[ht]
+  %\centerline{\includegraphics[width=10cm]{ATG/SPImplOpen}}
+%  \caption{Open Automaton of the Simple Protocol Implementation}  %\label{SimpleProtCounter:ImplOA}
+%\end{figure}
 
  \begin{figure}[ht]
-  %\centerline{\includegraphics[width=10cm]{ATG/SPImplOpen}}
-  \caption{Open Automaton of the Simple Protocol Implementation}  %\label{SimpleProtCounter:ImplOA}
-\end{figure}
-
-    \begin{figure}[ht]
-  \centerline{\includegraphics[width=10cm]{XFIG/SPImplOpen}}
+  \centerline{\includegraphics[width=15cm]{XFIG/SPImplOpen}}
   \caption{Open Automaton of the Simple Protocol Implementation}  \label{SimpleProtCounter:ImplOA}
@@
 
-    Figure \ref{SimpleProtCounter:ImplOA} shows the open automaton of the implementation $SimpleSystem$.
+    Figure \ref{SimpleProtCounter:ImplOA} shows the open automaton of the implementation $SimpleSystem$ (Figure \ref{SimpleProt:Impl}).
+    \RAB{In this drawing, we have short labels for states, representing $\ostate{s_0,m_0,r_0}$ by \texttt{000}.
+Note that open transitions are denoted $\texttt{OT}_i$ and tau open transition by  $\texttt{OT}_tau$.
+The resulting behavior is quite simple:  we have a main loop including receiving a message from $P$ and transmitting the same message to $Q$, with some intermediate $\tau$ actions from the internal communications between the protocol processes.
+In most of the transitions, you can observe that data is propagated between the successive state variables (holding the message, and the error counter value).
+On the right of the figure, you have a loop of $\tau$ actions showing the handling of errors and corresponding increments of the error counter.}
+
     \ERIC{In this drawing, we have short labels for states, representing $\ostate{s_0,m_0,r_0}$ by \texttt{000}.
@@
 \begin{figure}[ht]
-   \centerline{\includegraphics[width=7cm]{XFIG/WOT2-result}}
+   \centerline{\includegraphics[width=8cm]{XFIG/WOT2-result}}
   \caption{Construction of WOT2}
@@
 On the top we show the subset of the original open automaton (from Figure \ref{SimpleProtCounter:SpecOA}) considered here, and at the bottom the generated weak transition.
+\RAB{The weak open transition here is the transition delivering the result of the algorithm to hole $Q$ by applying or rules: \WTUn,\WTDeux, and \WTTrois.
+First rule \WTUn~ adds an $\texttt{WT}_\tau$ loop on each state.
+Rule \WTDeux~ transforms each 3 OTs into WOTs.
+Then consider application of Rule \WTTrois~ on a sequence 3  WOTs.
+$\openrule
+         {\{\}, True,
+			(\texttt{ec}\gets \texttt{ec}+1) }
+         {b1 \OTWeakarrow \tau b1}$; $\openrule
+         {\{\}, True,
+			(\texttt{ec}\gets \texttt{ec}+1) }
+         {b1 \OTWeakarrow \tau b1}$;  $\openrule
+         {\{\}, True,
+			() }
+         {b1 \OTWeakarrow \tau b1}$. Then Rule \WTTrois~ produces  $\openrule
+         {\{\}, True,
+			(\texttt{ec}\gets \texttt{ec}+2) }
+         {b1 \OTWeakarrow \tau b1}$. We can  can iterate this construction an arbitrary number of times, getting for any natural number $n$ the weak open transition:
+  $\openrule
+         {\emptyset, True,
+			(\texttt{ec}\gets \texttt{ec}+n) }
+         {b1 \OTWeakarrow \tau b1} \forall n \geq 0$.  Finally,  applying again \WTTrois, and using the central open transition having \texttt{q\_recv(ec)}  as $\alpha$, we get:
+      $\openrule
+         {\{Q\mapsto\texttt{q\_revc(ec)}\subst{ec\gets ec+n}\}, True,
+			(\texttt{ec}\gets \texttt{ec}+n) }
+         {b1 \OTWeakarrow {\texttt{out(m,ec)}\subst{ec\gets ec+n}} b0} \forall n \geq 0$. }
 
@@
          {s \OTWeakarrow {\texttt{out(m,ec)}\subst{ec\gets ec+n}} s'}$
+
 \end{example}
@@
 
-\begin{figure}[h]
-   \centerline{\includegraphics[width=13cm]{ATG/SPSpecWeakOpen}}
-  \caption{Weak Open Automaton of the Specification \TODO{out of date}}
-   \label{SimpleProtCounter:WeakSpecOA}
-\end{figure}
+%\begin{figure}[h]
+%   \centerline{\includegraphics[width=13cm]{ATG/SPSpecWeakOpen}}
+%  \caption{Weak Open Automaton of the Specification \TODO{out of date}}
+%   \label{SimpleProtCounter:WeakSpecOA}
+%\end{figure}
 

### 2020-02-12 2016-Weak-FH-Bisim/WeakBisim.tex
comments des figures

@@
 For instance, in the vector "$< \texttt{p\_send(m)},\texttt{in(m)},\_> \rightarrow \texttt{\underline{in(m)}}$ only $P$ and {\it PrefectBuffer} nodes are involved in the synchronization.
-More precisely, the synchronization between these processes occurs when  process $P$  performs $p\_send(m)$  action sending a message, and  the medium accepts the message through $\texttt{\texttt{in(m)}}$ action  at the same time.
+More precisely, the synchronization between these processes occurs when  process $P$  performs $\texttt{p\_send(m)}$  action sending a message, and  the medium accepts the message through $\texttt{in(m)}$ action  at the same time.
 And the result that will be returned at upper level is the internal action  $\texttt{\underline{in(m)}}$.
@@
  \[  OT_1  = \openrule{
-      \{P\mapsto p\_send(m)\},  [m=m'],  \{s1\_m\gets m\}
+      \{\texttt{P}\mapsto \texttt{p-send(m)}\},  [m=m'],  \{s1\_m\gets m\}
                       }
@@
     Figure \ref{SimpleProtCounter:ImplOA} shows the open automaton of the implementation $SimpleSystem$ (Figure \ref{SimpleProt:Impl}).
-    \RAB{In this drawing, we have short labels for states, representing $\ostate{s_0,m_0,r_0}$ by \texttt{000}.
-Note that open transitions are denoted $\texttt{OT}_i$ and tau open transition by  $\texttt{OT}_tau$.
+In this drawing, we have short labels for states, representing $\ostate{s_0,m_0,r_0}$ by \texttt{000}.
+Note that open transitions are denoted $\texttt{OT}_i$ and tau open transition by  $\texttt{OT}_{\tau}$.
 The resulting behavior is quite simple:  we have a main loop including receiving a message from $P$ and transmitting the same message to $Q$, with some intermediate $\tau$ actions from the internal communications between the protocol processes.
 In most of the transitions, you can observe that data is propagated between the successive state variables (holding the message, and the error counter value).
-On the right of the figure, you have a loop of $\tau$ actions showing the handling of errors and corresponding increments of the error counter.}
-
-    \ERIC{In this drawing, we have short labels for states, representing $\ostate{s_0,m_0,r_0}$ by \texttt{000}.
-For readability we only have written the \emph{external} actions of holes $P$ and $Q$ on the loop transitions of the first staes; they are also present on all other states.
-The resulting behavior is quite simple:  we have a main loop including receiving a message from $P$ and transmitting the same message to $Q$, with some intermediate $\tau$ actions from the internal communications between the protocol processes.
-In most of the transitions, you can observe that data is propagated between the successive state variables (holding the message, and the error counter value).
-On the right of the figure, you have a loop of $\tau$ transitions showing the handling of errors and corresponding increments of the error counter.}
+On the right of the figure, you have a loop of $\tau$ actions showing the handling of errors and corresponding increments of the error counter.
 
@@
 \begin{figure}[ht]
-   \centerline{\includegraphics[width=8cm]{XFIG/WOT2-result}}
-  \caption{Construction of WOT2}
+   \centerline{\includegraphics[width=10cm]{XFIG/WOT2-result}}
+  \caption{Construction of an example of weak open transition}
    \label{WOT2}
@@
 On the top we show the subset of the original open automaton (from Figure \ref{SimpleProtCounter:SpecOA}) considered here, and at the bottom the generated weak transition.
-\RAB{The weak open transition here is the transition delivering the result of the algorithm to hole $Q$ by applying or rules: \WTUn,\WTDeux, and \WTTrois.
+The weak open transition here is the transition delivering the result of the algorithm to hole $Q$ by applying or rules: \WTUn,\WTDeux, and \WTTrois.
 First rule \WTUn~ adds an $\texttt{WT}_\tau$ loop on each state.
@@
 			(\texttt{ec}\gets \texttt{ec}+n) }
-         {b1 \OTWeakarrow \tau b1} \forall n \geq 0$.  Finally,  applying again \WTTrois, and using the central open transition having \texttt{q\_recv(ec)}  as $\alpha$, we get:
+         {\text{b}1 \OTWeakarrow \tau b1} \forall n \geq 0$.  Finally,  applying again \WTTrois, and using the central open transition having \texttt{q-recv(ec)}  as $\alpha$, we get:
       $\openrule
-         {\{Q\mapsto\texttt{q\_revc(ec)}\subst{ec\gets ec+n}\}, True,
+         {\{\texttt{Q}\mapsto\texttt{q-revc(ec)}\subst{ec\gets ec+n}\}, True,
 			(\texttt{ec}\gets \texttt{ec}+n) }
-         {b1 \OTWeakarrow {\texttt{out(m,ec)}\subst{ec\gets ec+n}} b0} \forall n \geq 0$. }
-
-WOT2 here is the transition delivering the result of the algorithm to hole $Q$.
-Remark that it includes a loop increasing the error counter, occurring before the action of $Q$, and this action is using the resulting value of the counter.
-Let us go into the details, using rules WT1/2/3.
-First WT1 adds a $\tau$ loop on each state.
-Then consider application of Rule WT3 on a sequence 3 internal actions ``$\tau\subst{ec\gets ec+1};\tau\subst{ec\gets ec+1};\tau$''.
-Hole actions and predicates are empty, we just concentrate on the Post operations.
-Rule WT2 transforms each 3 OTs into WOTs.
-Then WT3 produces the weak OT:
-  $\openrule
-         {\{\}, True,
-			\subst{\texttt{ec++}\shortotimes\texttt{ec++}\shortotimes\emptyset} }
-         {s \OTWeakarrow {\tau\subst{\texttt{ec++}}} s'}$
-         that you can rewrite as:      
-  $\openrule
-         {\{\}, True,
-			\subst{ec\gets ec+2} }
-         {s \OTWeakarrow \tau s'}$
-
-         Now you can iterate this construction an arbitrary number of times, getting for any natural number $n$ the weak transition:
-  $\openrule
-         {\emptyset, True,
-			\subst{ec\gets ec+n} }
-         {s \OTWeakarrow \tau s'}$
-
-         For any of these, apply again WT3, using the central \texttt{q\_recv(ec)} transition as $\alpha$, and you get:
-      $\openrule
-         {\{Q\mapsto\texttt{q\_revc(ec)}\subst{ec\gets ec+n}\}, True,
-			\subst{ec\gets ec+n} }
-         {s \OTWeakarrow {\texttt{out(m,ec)}\subst{ec\gets ec+n}} s'}$
-
+         {b1 \OTWeakarrow {\underline{\texttt{out(m,ec)}}\subst{ec\gets ec+n}} b0} \forall n \geq 0$. 
 \end{example}

### 2020-02-12 2016-Weak-FH-Bisim/WeakBisim.tex
tr2, lemma2, double qed

@@
 	is verified and transforms assignments into post-conditions:		
-
-	\begin{description}
-		\item[{\TrUn:}]
-		$\inferrule
+\begin{mathpar}\inferrule
 		{ s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
@@
 			{\ostate{s} \OTarrow{\alpha} \ostate{s'}}
-		}
-		$
-	\end{description}
+		}\quad {\TrUn}
+\end{mathpar}
 %	Note that this note is greatly simplified by the fact that variables are local to 
@@
 	I_2$}.                                                                    
-
-	\begin{description}
-		\item[{\TrDeux:}]
-	\end{description}
-
-	\noindent
 \begin{mathpar}
@@
     	}
-    }
+    }\quad {\TrDeux}
 \end{mathpar}    
@@
 predicates:
-\begin{lemma}[Open transition decomposition]\label{lem-decompose} Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$}.
+\begin{lemma}[Open transition decomposition\label{lem-decompose}] Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$}.
 	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose:
@@
 $P[Q]_{j_0}$, assembling their predicates.
-\paragraph{Lemma~\ref{lem-compose}} {\bf Open transition composition}\\
+
+\begin{lemma}[Open transition composition]\label{lem-compose} 
 	Suppose $j_0\in J$ and:\\[-2ex]
@@
 	\]
+\end{lemma}
 
@@
 
+\TODO{LUDO: paragraphe d intro et de decription scientifique}
+
 We are currently extending this work,  looking at  both further properties of 
@@
        Definition~\ref{def:operationalSemantics}, applied to the pNet $P[Q]_{j_0}$. 	
-
-\noindent\TrDeux:\\
 	\noindent
@@
     	}
-    }
+    }\quad\TrDeux
 \end{mathpar}
@@
 
-\begin{lemma}[Open transition composition]\label{lem-compose} 
+\paragraph{\bf Lemma~\ref{lem-compose}} {\it Open transition composition}\\
 	Suppose $j_0\in J$ and:\\[-2ex]
@@
 	\]
-\end{lemma}
 
@@
 Definition~\ref{def:operationalSemantics}). Let $P=\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle$
-	\begin{description}
-		\item[{\TrDeux:}]
-	\end{description}
-
-	\noindent
 	\begin{small}
@@
     	}
-    }
+    }\quad \TrDeux
 \end{mathpar}  
@@
 \end{small}
- \qed
         \end{proof}
@@
  The obtained formula reaches the goal except for 
- two points:\\[-4.3ex] 
+ two points:
  \begin{itemize}
@@
 $\\
-This concludes the inductive step, showing  that the decomposition expressed by the $\Leftarrow$ direction of the lemma is always possible with the right side conditions. \qed
+This concludes the inductive step, showing  that the decomposition expressed by the $\Leftarrow$ direction of the lemma is always possible with the right side conditions. 
 \end{itemize}
@@
 (\forall j\in J.\gamma_j'=\gamma_j \land  \Pred \land \alpha=\alpha''  \land \Pred_{s',x}\subst{\Post_{OT}\uplus\Post\,}$\\
-\qed
 \end{proof}
@@
 %~~\qquad= \Post' \uplus \bigotimes_{j=n}^{0} \Post_j $\\
-\qed
+%\qed
 \end{proof}
@@
 \end{equation*}
-\qed
+%\qed
 \end{proof}
@@
 }
-This allows us to conclude concerning the lemma. \qed
+This allows us to conclude concerning the lemma. 
 \end{proof}
@@
 We conclude by observing that $\Post_P$ has no effect on variables of $Q$ and $Q'$, and thus on $\Pred_{Q,Q' x}$
-\qed
-
 % OLD
@@
 %	\]
-
  \end{proof}
@@
 We conclude by observing that $\Post_Q$ has no effect on variables of $P$ and $P'$, and thus on $\Pred_{P,P' x}$
-\qed
 \end{proof}

### 2020-02-12 2016-Weak-FH-Bisim/WeakBisim.tex
premiere tentative de conclusion

@@
 \label{section:conclusion}
-
-\TODO{LUDO: paragraphe d intro et de decription scientifique}
+ pNets (Parameterised Networks of Automata) is a formalism adapted to the representation of the behavior of a parallel or distributed systems.
+One  strength of pNets is their parameterized nature, making them adapted to the representation of systems of arbitrary size, and making the modelling of parameterized system possible.
+Parameters are also crucial to reason on interaction protocols that can address one entity inside an indexed set of processes.
+This article focuses on open pNets that can represent process at the same time composition operators and
+protocols synchronizing the actions of processes that can be plugged afterwards. Open
+pNets can be defined as hierarchical composition of automata with holes and parameters. We
+defined here a semantics for open pNets and a complete bisimulation theory for them.
+
+The semantics of open pNets relies on the definition of open automata that are automata with holes and parameters, but no hierarchy.
+Open automata are somehow labelled transition systems with parameters and holes, a notion that is useful to define semantics, but makes less sense when modelling a system, compared to pNets.
+To be precise, it is on open automata that we define our bisimulation relations.
+
+This articles defines a strong and a weak bisimulation principles that are adapted to parameterized systems and hierarchical composition.
+Our bisimulation principles handle pNets parameters in the sense that two states might be or not in relation depending on the value of parameters.
+Our strong  bisimulation is compositional by nature in the sense that bisimulation is maintained when composing processes.
+We also identified a simple and realistic condition on the semantics of non-observable actions that allows weak bisimulation to be also compositional.
+Overall we believe that this article paved the way for a solid theoretical foundation for compositional verification of parallel and distributed systems.
 

### 2020-02-17 2016-Weak-FH-Bisim/WeakBisim.tex
petite passe sur conclu

@@
 Parameters are also crucial to reason on interaction protocols that can address one entity inside an indexed set of processes.
-This article focuses on open pNets that can represent process at the same time composition operators and
-protocols synchronizing the actions of processes that can be plugged afterwards. Open
-pNets can be defined as hierarchical composition of automata with holes and parameters. We
+pNets have been successfully used to represent behavioural specification of parallel and distributed components and verify their correctness~\cite{AmeurBoulifa2017,HKM-FASE16}.
+VCE is the specification and verification platform that uses pNets as an intermediate representation.
+
+Open pNets are pNets with holes; they are adapted to represent processes parameterized by the behaivour of other processes, like composition operators or interaction 
+protocols that synchronize the actions of processes that can be plugged afterwards. Open
+pNets are hierarchical composition of automata with holes and parameters. We
 defined here a semantics for open pNets and a complete bisimulation theory for them. 
-
 The semantics of open pNets relies on the definition of open automata that are automata with holes and parameters, but no hierarchy.
@@
 
-This articles defines a strong and a weak bisimulation principles that are adapted to parameterized systems and hierarchical composition.
+This articles defined a strong and a weak bisimulation principles that are adapted to parameterized systems and hierarchical composition.
 Our bisimulation principles handle pNets parameters in the sense that two states might be or not in relation depending on the value of parameters.
@@
 \ERIC{
-  => Context VCE, ref to FASE paper, citer Avocs et  PEPM\\
+  =>  citer Avocs et  PEPM\\
 => Simplification is mostly implemented. It is not strictly required for the Open Automaton construction, but it will be critical later for predicate comparison in the bisimulation algorithm.}

### 2020-02-17 2016-Weak-FH-Bisim/WeakBisim.tex
improvement presentation theorem in appendix

@@
 \end{theorem}
-The proof  is detailed in \ref{app-WFH-equiv}, it follows a similar pattern as the proof that strong FH-bisimulation is an equivalence, but technical details are different, and in practice we rely on a different (but proven equivalent) definition of weak FH-bisimilarity; this equivalent version simulates a \emph{weak} open transition with a set of weak open transition.
+The proof  is detailed in Appendix \ref{app-WFH-equiv}, it follows a similar pattern as the proof that strong FH-bisimulation is an equivalence, but technical details are different, and in practice we rely on a different (but proven equivalent) definition of weak FH-bisimilarity; this equivalent version simulates a \emph{weak} open transition with a set of weak open transition.
 The careful use of the best definition of weak FH-bisimilarity makes the proof similar to the strong FH-bisimulation case.
@@
 	$\pNet'[\pNetQ']_{j}$ are weak FH-bisimilar. This can be shown by proving the two following theorems.
+The detailed proof of these theorem can be found in Appendix~\ref{sec:app-composition}.
+The proof strongly relies on the fact that weak FH-bisimulation is an equivalence, but also on the composition properties for open automata.
 
@@
 \end{theorem}
-
-The detailed proof of these theorem can be found in~\ref{app-WFH-equiv}.
-The proof strongly relies on the fact that weak FH-bisimulation is an equivalence, but also on the composition properties for open automata.
 
@@
 
-\begin{lemma}
+\begin{lemma}[Alternative definition of weak open transitions]
 \label{lem-rel-OT-WOT} Let $A = <J,\mathcal{S}, s_0,
@@
 
-\begin{lemma}\label{lem-alternative-weak-bisim} The definition of weak bisimulation given in Definition \ref{def-Weak-bisim} is equivalent to the following one:
+\begin{lemma}[Alternative definition of weak bisimulation]\label{lem-alternative-weak-bisim} The definition of weak bisimulation given in Definition \ref{def-Weak-bisim} is equivalent to the following one:
 
@@
 
-\TODO{attention theorem 10 est le thm 6 en fait -- presentation des thm et preuve a revoir}
-\begin{theorem}[Weak FH-Bisimulation is an equivalence]\label{thm-weak-equiv} Suppose $\mathcal{R}$ 
+%\begin
+\noindent{\bf Theorem~\ref{thm-weak-equiv}}. \emph{Weak FH-Bisimulation is an equivalence}.
+ Suppose $\mathcal{R}$ 
 is a weak FH-bisimulation. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
 reflexive, symmetric and transitive.
-\end{theorem}
+%\end{theorem}
 
@@
 By construction the concatenation of these elements is $\gamma_{tj}$, for $t\in[0..n]$.
-$\Post_{ik}$ has no effect on $\gamma_{tj}$ but  $\Post_{k}$ has \TODO{do we want to be more explicit in the explanation?
-giving the exact indices is cumbersome because Post'ij is either empty or postij for the same indices as gamma, this can also be related with the ni and n'i}:\\
+$\Post_{ik}$ has no effect on $\gamma_{tj}$ but  $\Post_{k}$ has.
+%\TODO{do we want to be more explicit in the explanation?
+giving the exact indices is cumbersome because Post'ij is either empty or postij for the same indices as gamma, this can also be related with the ni and n'i}
+We obtain:\\
 
@@
 
-\newpage
-
-\begin{theorem}[Congruence]\label{thm-congr-weq}
+%\newpage
+
+%\begin
+\noindent
+{\bf Theorem~\ref{weak-thm-congr-eq}}. \emph{Congruence}.
 	Consider an open pNet:
@@
 	$\pNet[\pNetQ']_{j_0}$ are weak FH-bisimilar.
-\end{theorem}
+%\end{theorem}
  \begin{proof}  Consider $Q$ weak FH-bisimilar to $Q'$.
@@
  \end{proof}
-\begin{theorem}[Context equivalence]\label{thm-ctxt-weq}
-	Consider two FH-bisimilar open pNets:
+
+\noindent {\bf Theorem~\ref{weak-thm-ctxt-eq}}. \emph{Context equivalence}.
+	Consider two FH-bisimilar open pNets:\\
 	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
@@
 	$\pNet'[Q]_{j_0}$ are FH-bisimilar.
-\end{theorem}
+%\end{theorem}
 
@@
 
-We here need a special case of Lemma\ref{lem-Weakcompose}where the inner pNet $Q$ does a simple OT.
+We here need a special case of Lemma~\ref{lem-Weakcompose} where the inner pNet $Q$ does a simple OT.
 This is just a particular case of the theorem but where notations get simplified because the inner pnet does a single transition.

### 2020-02-18 2016-Weak-FH-Bisim/WeakBisim.tex
corrections de jeudi dernier...

@@
 argument, through the two protocol entities.
-Process $P$ send an $\texttt{p\_send(m)}$ message to the $Sender$; this communication is denoted as $\texttt{\underline{in(m)}}$, where underline actions represent internal actions (similar to the $\tau$ of CCS), that cannot be further synchronised with the environment.
+Process $P$ send an $\texttt{p-send(m)}$ message to the $Sender$; this communication is denoted as $\texttt{\underline{in(m)}}$, where underline actions represent internal actions (similar to the $\tau$ of CCS), that cannot be further synchronised with the environment.
 At the other end process $Q$ receives the message from the $Receiver$.
-The holes $P$ and $Q$ can also have other interactions with their environment, represented here by actions $\texttt{p\_a}$ and $\texttt{q\_b}$.
+The holes $P$ and $Q$ can also have other interactions with their environment, represented here by actions $\texttt{p-a}$ and $\texttt{q-b}$.
 The underlying network is modelled by a medium entity transporting messages from the sender to the receiver, and that is able to detect transport errors, and signal them to the sender.
@@
 Nodes of the tree are synchronized using four synchronization vectors, that  express the possible synchronization between the parameterized actions of a subset of the nodes.
-For instance, in the vector "$< \texttt{p\_send(m)},\texttt{in(m)},\_> \rightarrow \texttt{\underline{in(m)}}$ only $P$ and {\it PrefectBuffer} nodes are involved in the synchronization.
-More precisely, the synchronization between these processes occurs when  process $P$  performs $\texttt{p\_send(m)}$  action sending a message, and  the medium accepts the message through $\texttt{in(m)}$ action  at the same time.
+For instance, in the vector "$< \texttt{p-send(m)},\texttt{in(m)},\_> \rightarrow \texttt{\underline{in(m)}}$ only $P$ and {\it PrefectBuffer} nodes are involved in the synchronization.
+More precisely, the synchronization between these processes occurs when  process $P$  performs $\texttt{p-send(m)}$  action sending a message, and  the medium accepts the message through $\texttt{in(m)}$ action  at the same time.
 And the result that will be returned at upper level is the internal action  $\texttt{\underline{in(m)}}$.
@@
 On the top we show the subset of the original open automaton (from Figure \ref{SimpleProtCounter:SpecOA}) considered here, and at the bottom the generated weak transition.
-The weak open transition here is the transition delivering the result of the algorithm to hole $Q$ by applying or rules: \WTUn,\WTDeux, and \WTTrois.
+The weak open transition shown here is the transition delivering the result of the algorithm to hole $Q$ by applying rules: \WTUn,\WTDeux, and \WTTrois.
 First rule \WTUn~ adds an $\texttt{WT}_\tau$ loop on each state.
@@
 
-%% \TODO{Eric: insert here a table with the details of the WOTs.Il manque encore au moins 3 WOT dans ce dessin...}
-
-%% \smallskip
-%% $1^st$ try, user-friendly style:
-
-%% $$ 3 = \tau^*; \underline{in(m)}\{s1\_c:=0, s1\_m:=m\}; \tau\{s1\_c++\}^*$$
-
-%% \smallskip
-%% $2^nd$ try, full formal style ?:
-%% \medskip
-
 Now let us give some details about the construction of the weak automaton of the implementation pNet, obtained by application of the weak rules as explained above.
@@
 
-$post_3 = (\texttt{s1\_c}\gets 0, \texttt{s1\_m}\gets \texttt{m})$
-
-$post_4 = (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_c}\gets \texttt{s1\_c})$
-
-$post_5 = (\texttt{m2\_c}\gets \texttt{m1\_c})$
-
-$post_6 = (\texttt{s1\_c}\gets \texttt{m2\_c+1})$
-
-$post_7 = (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_c}\gets \texttt{m1\_c})$
+$post_3 = (\texttt{s1\_ec}\gets 0, \texttt{s1\_m}\gets \texttt{m})$
+
+$post_4 = (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec})$
+
+$post_5 = (\texttt{m2\_ec}\gets \texttt{m1\_ec})$
+
+$post_6 = (\texttt{s1\_ec}\gets \texttt{m2\_ec+1})$
+
+$post_7 = (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_ec}\gets \texttt{m1\_ec})$
 
@@
 $Post_{456} = post_6 \shortotimes\ post_5 \shortotimes\ post_4
-= (\texttt{s1\_c}\gets \texttt{s1\_c}+1)$.
+= (\texttt{s1\_ec}\gets \texttt{s1\_ec}+1)$.
 \medskip
 
-So if we denote ${Post_{456}}^*$ any iteration of this loop, we get ${Post_{456}}^* = (\texttt{s1\_c}\gets \texttt{s1\_c}+n)$ for any $n\ge 0$, and we will get e.g.
-the Post of the weak OT number 3' as $ post_4\shortotimes {Post_{456}}^*\shortotimes\ post_3 = (\texttt{m1\_msg}\gets m, \texttt{m1\_c}\gets n), \forall n\ge 0$
+So if we denote ${Post_{456}}^*$ any iteration of this loop, we get ${Post_{456}}^* = (\texttt{s1\_ec}\gets \texttt{s1\_ec}+n)$ for any $n\ge 0$, and we will get e.g.
+the Post of the weak OT number 3' as $ post_4\shortotimes {Post_{456}}^*\shortotimes\ post_3 = (\texttt{m1\_msg}\gets m, \texttt{m1\_ec}\gets n), \forall n\ge 0$
 \medskip
 
-We can now show some of the weak OTs of Figure \ref{SimpleProtCounter:SpecOA-partial} (the full table will be included in Appendix \ref{Appendix:FullExample}) :
+We can now show some of the weak OTs of Figure \ref{SimpleProtCounter:SpecOA-partial} (the full table is included in Appendix \ref{Appendix:FullExample}) :
 \smallskip
@@
 $ 1 = \openrule
-{\{\texttt{P}\mapsto \texttt{p\_a}\}, [\forall \texttt{m}. \texttt{p\_a} \neq \texttt{p\_send(m)} ], ()}
+{\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], ()}
 {000 \OTWeakarrow {\tau} 000}$
 
-$ 2 = \openrule
-{\{\texttt{Q}\mapsto \texttt{q\_b}\}, [\forall \texttt{m}. \texttt{q\_b} \neq \texttt{q\_recv(m)} ], ()}
-{000 \OTWeakarrow {\tau} 000}$
-
-$ 3 = \openrule
-  {\{\texttt{P}\mapsto \texttt{p\_send(m)}\}, True,
-    (\texttt{s1\_msg}\gets m, \texttt{s1\_c}\gets n)}
-  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
-  \ \forall n\ge 0$
-
 $ 3' = \openrule
-  {\{\texttt{P}\mapsto \texttt{p\_send(m)}\}, True,
-    (\texttt{m1\_msg}\gets m, \texttt{m1\_c}\gets n)}
+  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
+    (\texttt{m1\_msg}\gets m, \texttt{m1\_ec}\gets n)}
   {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 210}
@@
 
-$ 3'' = \openrule
-  {\{\texttt{P}\mapsto \texttt{p\_send(m)}\}, True, 
-    (\texttt{m2\_c}\gets n)}
-  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 220}
-  \ \forall n\ge 0$
-
          $ 4 = \openrule
-         {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_c}\gets \texttt{s1\_c}+n)}
+         {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n)}
          {100 \OTWeakarrow {\tau} 210}
@@
 
-$ 5 = \openrule
-         {\{\}, True, (\texttt{m2\_c}\gets \texttt{m1\_c}+n)}
-         {210 \OTWeakarrow {\tau} 220}
-         \ \forall n\ge 0$
-
-$ 6 = \openrule
-         {\{\}, True, (\texttt{s1\_c}\gets \texttt{m2\_c}+n)}
-         {220 \OTWeakarrow {\tau} 100}
-         \ \forall n\ge 0$
-
-$ 7 = \openrule
-         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_c}\gets \texttt{s1\_c}+n)}
-         {100 \OTWeakarrow {\tau} 201}
-         \ \forall n\ge 0$
-
-$ 7' = \openrule
-         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_c}\gets \texttt{m1\_c}+n)}
-         {210 \OTWeakarrow {\tau} 201}
-         \ \forall n\ge 0$
-
-$ 7'' = \openrule
-         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_c}\gets \texttt{m2\_c}+n)}
-         {220 \OTWeakarrow {\tau} 201}
-         \ \forall n\ge 1$
-
 $ 8 = \openrule
          {\{\}, True, ()}
-         {201 \OTWeakarrow {\underline{\texttt{out(m,c)}}\subst{(m\gets \texttt{r1\_msg}, c\gets \texttt{r1\_c}}} 202}
+         {201 \OTWeakarrow {\underline{\texttt{out(m,c)}}\subst{(m\gets \texttt{r1\_msg}, c\gets \texttt{r1\_ec}}} 202}
          $
 
-\newpage
 \subsection{Composition properties: composition of weak open transitions}
@@
 state a0
-transition m_recv(msg,c) -> a1 {a1_msg:=msg, a1_c:=c}
+transition m_recv(msg,c) -> a1 {a1_msg:=msg, a1_ec:=c}
 
 state a1
-vars a1_msg:Data a1_c:Int
-transition m_send(a1_msg, a1_c) -> a0 
+vars a1_msg:Data a1_ec:Int
+transition m_send(a1_msg, a1_ec) -> a0 
 transition synchro($tau) -> a2
@@
 state s0
-transition s_recv(msg) -> s1 {s1_msg:=msg, s1_c:=0}
+transition s_recv(msg) -> s1 {s1_msg:=msg, s1_ec:=0}
 
 state s1
-vars s1_msg:Data s1_c:Int
-transition s_send(s1_msg, s1_c) -> s2 {s2_c:=s1_c}
+vars s1_msg:Data s1_ec:Int
+transition s_send(s1_msg, s1_ec) -> s2 {s2_ec:=s1_ec}
 
 state s2
-vars  s2_c:Int
+vars  s2_ec:Int
 transition $s_ack -> s0
-transition $s_error -> s1 {s1_c:=s2_c+1}
+transition $s_error -> s1 {s1_ec:=s2_ec+1}
 
@@
 state r0
-transition r_recv(msg,c) -> r1 {r1_msg:=msg, r1_c:=c}
+transition r_recv(msg,c) -> r1 {r1_msg:=msg, r1_ec:=c}
 
 state r1
-vars r1_msg:Data r1_c:Int
-transition r_send(r1_msg, r1_c) -> r2
+vars r1_msg:Data r1_ec:Int
+transition r_send(r1_msg, r1_ec) -> r2
 
@@
 %% - pLTS: Sender
-%% - - Transition: s0---in(msg)-->s1, { s1_msg := msg s1_c := 0}
-%% - - Transition: s1---s_send(s1_msg, s1_c)-->s2, {}
+%% - - Transition: s0---in(msg)-->s1, { s1_msg := msg s1_ec := 0}
+%% - - Transition: s1---s_send(s1_msg, s1_ec)-->s2, {}
 %% - - Transition: s2---s_ack-->s0, {}
-%% - - Transition: s2---s_error-->s1, { s1_c := s2_c+1}
-%% - - Variable: s1_c, State: s1, Value(s) = 0,s2_c+1,
+%% - - Transition: s2---s_error-->s1, { s1_ec := s2_ec+1}
+%% - - Variable: s1_ec, State: s1, Value(s) = 0,s2_ec+1,
 %% - - Variable: s1_msg, State: s1, Value(s) = msg,
 %% - pLTS: M1
-%% - - Transition: a0---m_recv(msg, c)-->a1, { a1_msg := msg a1_c := c}
-%% - - Transition: a1---m_send(a1_msg, a1_c)-->a0, {}
+%% - - Transition: a0---m_recv(msg, c)-->a1, { a1_msg := msg a1_ec := c}
+%% - - Transition: a1---m_send(a1_msg, a1_ec)-->a0, {}
 %% - - Transition: a1---_tau_-->a2, {}
@@
 %% - - Variable: a1_msg, State: a1, Value(s) = msg,
-%% - - Variable: a1_c, State: a1, Value(s) = c,
+%% - - Variable: a1_ec, State: a1, Value(s) = c,
 %% - pLTS: Receiver
-%% - - Transition: r0---r_recv(msg, c)-->r1, { r1_msg := msg r1_c := c}
-%% - - Transition: r1---out(r1_msg, r1_c)-->r2, {}
+%% - - Transition: r0---r_recv(msg, c)-->r1, { r1_msg := msg r1_ec := c}
+%% - - Transition: r1---out(r1_msg, r1_ec)-->r2, {}
 %% - - Transition: r2---r_ack-->r0, {}
 %% - - Variable: r1_msg, State: r1, Value(s) = msg,
-%% - - Variable: r1_c, State: r1, Value(s) = c,
+%% - - Variable: r1_ec, State: r1, Value(s) = c,
 %% Holes: Q
@@
 {P|->p_send(m:SV6:1:1)},
-[(msg=m:SV0:12:1)/\((s_recv(msg))=(s_recv(m:SV0:12:1)))], {s1_msg := msg, s1_c := 0}
+[(msg=m:SV0:12:1)/\((s_recv(msg))=(s_recv(m:SV0:12:1)))], {s1_msg := msg, s1_ec := 0}
 	OT:1 ------------------------------------------------------------
@@
 
-{},   [(s1_msg=m:SV1:114:2)/\(s1_c=c:SV1:114:2)
-  /\((s_send(s1_msg, s1_c))=(s_send(m:SV1:114:2, c:SV1:114:2)))
+{},   [(s1_msg=m:SV1:114:2)/\(s1_ec=c:SV1:114:2)
+  /\((s_send(s1_msg, s1_ec))=(s_send(m:SV1:114:2, c:SV1:114:2)))
   /\(msg=m:SV1:114:2)/\(c=c:SV1:114:2)
   /\((m_recv(msg, c))=(m_recv(m:SV1:114:2, c:SV1:114:2)))],
-{s2_c := s1_c, a1_msg := msg, a1_c := c}
+{s2_ec := s1_ec, a1_msg := msg, a1_ec := c}
 	OT:6 ------------------------------------------------------------
@@
 
-{},   [(a1_msg=m:SV2:114:3)/\(a1_c=c:SV2:114:3)
-  /\((m_send(a1_msg, a1_c))=(m_send(m:SV2:114:3, c:SV2:114:3)))
+{},   [(a1_msg=m:SV2:114:3)/\(a1_ec=c:SV2:114:3)
+  /\((m_send(a1_msg, a1_ec))=(m_send(m:SV2:114:3, c:SV2:114:3)))
   /\(msg=m:SV2:114:3)/\(c=c:SV2:114:3)
   /\((r_recv(msg, c))=(r_recv(m:SV2:114:3, c:SV2:114:3)))],
-{r1_msg := msg, r1_c := c}
+{r1_msg := msg, r1_ec := c}
 	OT:9 ------------------------------------------------------------
@@
 {Q|->q_recv(m:SV8:1:3, c:SV8:1:3)},
-[(r1_msg=m:SV5:18:6)/\(r1_c=c:SV5:18:6)
-  /\((r_send(r1_msg, r1_c))=(r_send(m:SV5:18:6, c:SV5:18:6)))],   {}
+[(r1_msg=m:SV5:18:6)/\(r1_ec=c:SV5:18:6)
+  /\((r_send(r1_msg, r1_ec))=(r_send(m:SV5:18:6, c:SV5:18:6)))],   {}
 	OT:12 ------------------------------------------------------------
@@
 
-		{},   [],   {s1_c := s2_c+1}
+		{},   [],   {s1_ec := s2_ec+1}
 	OT:16 --------------------------------------
@@
 ===================
-pLTS States: <s1 vars: { s1_msg <-{msg} s1_c <-{0, s2_c+1}}> <a0 vars: {}> <r0 vars: {}>
+pLTS States: <s1 vars: { s1_msg <-{msg} s1_ec <-{0, s2_ec+1}}> <a0 vars: {}> <r0 vars: {}>
 
@@
 ===================
-pLTS States: <s2 vars: { s2_c <-{s1_c}}> <a1 vars: { a1_msg <-{msg} a1_c <-{c}}> <r0 vars: {}>
+pLTS States: <s2 vars: { s2_ec <-{s1_ec}}> <a1 vars: { a1_msg <-{msg} a1_ec <-{c}}> <r0 vars: {}>
 
@@
 ===================
-pLTS States: <s2 vars: { s2_c <-{s1_c}}> <a0 vars: {}> <r1 vars: { r1_c <-{c} r1_msg <-{msg}}>
+pLTS States: <s2 vars: { s2_ec <-{s1_ec}}> <a0 vars: {}> <r1 vars: { r1_ec <-{c} r1_msg <-{msg}}>
 
@@
 ===================
-pLTS States: <s2 vars: { s2_c <-{s1_c}}> <a2 vars: {}> <r0 vars: {}>
+pLTS States: <s2 vars: { s2_ec <-{s1_ec}}> <a2 vars: {}> <r0 vars: {}>
 
@@
 ===================
-pLTS States: <s2 vars: { s2_c <-{s1_c}}> <a0 vars: {}> <r2 vars: {}>
+pLTS States: <s2 vars: { s2_ec <-{s1_ec}}> <a0 vars: {}> <r2 vars: {}>
 
@@
 %%<s2\_a0\_r0>, encoding the loop.
+
+\begin{figure}[h]
+   \centerline{\includegraphics[width=9cm]{XFIG/SimpleProtImpl-WOA}}
+  \caption{Weak Open Automaton of the implementation}
+   \label{Appendix:SpecOA-partial}
+\end{figure}
+
+In Figure \ref{Appendix:SpecOA-partial} we show the weak oepn automaton of our implementation pNet. Details of the weak transitions is listed here:
+
+$ 1 = \openrule
+{\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], ()}
+{000 \OTWeakarrow {\tau} 000}$
+
+$ 2 = \openrule
+{\{\texttt{Q}\mapsto \texttt{q-b}\}, [\forall \texttt{m}. \texttt{q-b} \neq \texttt{q-recv(m)} ], ()}
+{000 \OTWeakarrow {\tau} 000}$
+
+$ 3 = \openrule
+  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
+    (\texttt{s1\_msg}\gets m, \texttt{s1\_ec}\gets n)}
+  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
+  \ \forall n\ge 0$
+
+$ 3' = \openrule
+  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
+    (\texttt{m1\_msg}\gets m, \texttt{m1\_ec}\gets n)}
+  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 210}
+  \ \forall n\ge 0$
+
+$ 3'' = \openrule
+  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True, 
+    (\texttt{m2\_ec}\gets n)}
+  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 220}
+  \ \forall n\ge 0$
+
+         $ 4 = \openrule
+         {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n)}
+         {100 \OTWeakarrow {\tau} 210}
+         \ \forall n\ge 0$
+
+$ 5 = \openrule
+         {\{\}, True, (\texttt{m2\_ec}\gets \texttt{m1\_ec}+n)}
+         {210 \OTWeakarrow {\tau} 220}
+         \ \forall n\ge 0$
+
+$ 6 = \openrule
+         {\{\}, True, (\texttt{s1\_ec}\gets \texttt{m2\_ec}+n)}
+         {220 \OTWeakarrow {\tau} 100}
+         \ \forall n\ge 0$
+
+$ 7 = \openrule
+         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s1\_ec}+n)}
+         {100 \OTWeakarrow {\tau} 201}
+         \ \forall n\ge 0$
+
+$ 7' = \openrule
+         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_ec}\gets \texttt{m1\_ec}+n)}
+         {210 \OTWeakarrow {\tau} 201}
+         \ \forall n\ge 0$
+
+$ 7'' = \openrule
+         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_ec}\gets \texttt{m2\_ec}+n)}
+         {220 \OTWeakarrow {\tau} 201}
+         \ \forall n\ge 1$
+
+$ 8 = \openrule
+         {\{\}, True, ()}
+         {201 \OTWeakarrow {\underline{\texttt{out(m,c)}}\subst{(m\gets \texttt{r1\_msg}, c\gets \texttt{r1\_ec}}} 202}
+         $
 

### 2020-02-19 2016-Weak-FH-Bisim/WeakBisim.tex
Renomme WT_n

@@
 
-\TODO{voisr si on redefinit les bigotimes pour prendre des maps et retourner des maps au lieu des substitutions (et on englobe dans une subst a la fin)}
-
-\TODO{prendre soin des posts sur les actions partout}
-
-===> dealine 14 Juillet
-
-TODOs du 19 decembre
-
-- enlever 5.2 et citer avocs
-
-- ajouter des proof sketch dans le papier
-
-- def 11 point 2:
-A, Pred, Post
------------   in T
-s->s'
-et A(j)=tau
-implies blablabla
-
-OLD OLD OLD (check)
-Notes de reunion 24 Sept
-
-- etat de l art: il faudrait des refs sur bisim en gemneral, probablement avec pas mal de pi calcul (Eric?), des refs sur pourquoi pnets et des refs sur utilite de la weak bisim en verif
-
-- target: JLamp
-
-Conventions
-[14/9/2018]
-
-Dans le texte pas de $\backslash$ devant pNet et pLTS
-
-pNet devient P ou Q dans les equations; on garde $pLTS$
-
-\medskip
-
-TODOS et deadline
-
-Global and questions:
-\begin{itemize}
-\item \TODO{should we use iff/implies or LeftRightArrow/Rightarrow}
-\item related works
-\end{itemize}
-Ludo:
-\begin{itemize}
-\item[X] reorga sec weak bisim + thm -> 10 Juil
-\item[X]  intro et orga globale du papier -> fin aout
-\item[partial] explication dans semantique open pnets et composition
-\item uniformisation pNet P Q
-\end{itemize}
+%% \TODO{voisr si on redefinit les bigotimes pour prendre des maps et retourner des maps au lieu des substitutions (et on englobe dans une subst a la fin)}
+
+%% \TODO{prendre soin des posts sur les actions partout}
+
+%% ===> dealine 14 Juillet
+
+%% TODOs du 19 decembre
+
+%% - enlever 5.2 et citer avocs
+
+%% - ajouter des proof sketch dans le papier
+
+%% - def 11 point 2:
+%% A, Pred, Post
+%% -----------   in T
+%% s->s'
+%% et A(j)=tau
+%% implies blablabla
+
+%% OLD OLD OLD (check)
+%% Notes de reunion 24 Sept
+
+%% - etat de l art: il faudrait des refs sur bisim en gemneral, probablement avec pas mal de pi calcul (Eric?), des refs sur pourquoi pnets et des refs sur utilite de la weak bisim en verif
+
+%% - target: JLamp
+
+%% Conventions
+%% [14/9/2018]
+
+%% Dans le texte pas de $\backslash$ devant pNet et pLTS
+
+%% pNet devient P ou Q dans les equations; on garde $pLTS$
+
+%% \medskip
+
+%% TODOS et deadline
+
+%% Global and questions:
+%% \begin{itemize}
+%% \item \TODO{should we use iff/implies or LeftRightArrow/Rightarrow}
+%% \item related works
+%% \end{itemize}
+%% Ludo:
+%% \begin{itemize}
+%% \item[X] reorga sec weak bisim + thm -> 10 Juil
+%% \item[X]  intro et orga globale du papier -> fin aout
+%% \item[partial] explication dans semantique open pnets et composition
+%% \item uniformisation pNet P Q
+%% \end{itemize}
 
@@
   \begin{example}
-    Figures \ref{SimpleProtCounter:WeakSpecOA} and \ref{SimpleProtCounter:SpecOA-partial} respectively show the weak automata of the simple protocol specification and implementation.
+    Figures \ref{SimpleProtCounter:WeakSpecOA} and \ref{SimpleProtCounter:ImplOA} respectively show the weak automata of the simple protocol specification and implementation.
     \TODO{comment...}
+
+    For readability, we did not include the full details of the Implementation weak open transitions in Figure \ref{SimpleProtCounter:ImplOA}, they will appear below.
+In this automaton, many WOT are similar, and numbered accordingly as 3, 3', 3'', and 8, 8', 8'' respectively: they only differ by the name of the state variables in their respective source or target states.
 \end{example}
@@
   \caption{Weak Open Automaton of the implementation}
-   \label{SimpleProtCounter:SpecOA-partial}
+   \label{SimpleProtCounter:ImplOA}
 \end{figure}

### 2020-02-19 2016-Weak-FH-Bisim/WeakBisim.tex
Fini Fig 7

@@
 \begin{figure}[h]
-   \centerline{\includegraphics[width=9cm]{XFIG/SimpleProtImpl-WOA}}
+   \centerline{\includegraphics[width=11cm]{XFIG/SimpleProtImpl-WOA}}
   \caption{Weak Open Automaton of the implementation}
@@
 
-We can now show some of the weak OTs of Figure \ref{SimpleProtCounter:SpecOA-partial} (the full table is included in Appendix \ref{Appendix:FullExample}) :
+We can now show some of the weak OTs of Figure \ref{SimpleProtCounter:ImplOA} (the full table is included in Appendix \ref{Appendix:FullExample}) :
 \smallskip
 
-$ 1 = \openrule
+$ WT_1 = \openrule
 {\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], ()}
@@
 
-$ 3' = \openrule
+$ WT_{3'} = \openrule
   {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
-    (\texttt{m1\_msg}\gets m, \texttt{m1\_ec}\gets n)}
+    (\texttt{m1\_msg}\gets \texttt{m}, \texttt{m1\_ec}\gets n)}
   {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 210}
@@
 
-         $ 4 = \openrule
+         $ WT_4 = \openrule
          {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n)}
@@
 
-$ 8 = \openrule
+$ WT_8 = \openrule
          {\{\}, True, ()}
-         {201 \OTWeakarrow {\underline{\texttt{out(m,c)}}\subst{(m\gets \texttt{r1\_msg}, c\gets \texttt{r1\_ec}}} 202}
+         {201 \OTWeakarrow {\underline{\texttt{out(r1-msg,r1-ec)}}} 202}
          $

### 2020-02-21 2016-Weak-FH-Bisim/WeakBisim.tex

--- 2020-02-19 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
+    \TODO{introduce the notation for parametrized OTs}
+
     For readability, we did not include the full details of the Implementation weak open transitions in Figure \ref{SimpleProtCounter:ImplOA}, they will appear below.
-In this automaton, many WOT are similar, and numbered accordingly as 3, 3', 3'', and 8, 8', 8'' respectively: they only differ by the name of the state variables in their respective source or target states.
+    First, we the weak OT loops on state $ostate{000}$ are also present in all other states, we did not repeat them.
+Then many WOTs are similar, and numbered accordingly as 3, 3', 3'', and 8, 8', 8'',8''' respectively: they only differ by the name of the state variables in their respective source or target states.
 \end{example}
@@
 Now let us give some details about the construction of the weak automaton of the implementation pNet, obtained by application of the weak rules as explained above.
-Here we denote as $post_n$ the effect (= substitution) of the strong open transition $OT_n$ from Figure \ref{SimpleProtCounter:ImplOA}:
+We concentrate on transitions $WT_3$ and $WT_4$.
+Let us denote as $post_n$ the effect (= substitution) of the strong open transitions $OT_n$ from Figure \ref{SimpleProtCounter:ImplOA}:
 \smallskip
 
-$post_1 = post_2 = ()$
-
 $post_3 = (\texttt{s1\_ec}\gets 0, \texttt{s1\_m}\gets \texttt{m})$
@@
 
-$post_7 = (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_ec}\gets \texttt{m1\_ec})$
-
-$post_8 = post_9 = ()$
 \medskip
@@
 
-We can now show some of the weak OTs of Figure \ref{SimpleProtCounter:SpecOA-partial} (the full table is included in Appendix \ref{Appendix:FullExample}) :
+We can now show some of the weak OTs of Figure \ref{SimpleProtCounter:ImplOA} (the full table is included in Appendix \ref{Appendix:FullExample}) :
 \smallskip
 
-$ 1 = \openrule
+$ WI_1 = \openrule
 {\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], ()}
@@
 
-$ 3' = \openrule
+$ WI_3(n) = \openrule
   {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
-    (\texttt{m1\_msg}\gets m, \texttt{m1\_ec}\gets n)}
-  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 210}
+    (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets n)}
+  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
   \ \forall n\ge 0$
 
-         $ 4 = \openrule
+  $ WI_4(n) = \openrule
          {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n)}
@@
 
-$ 8 = \openrule
-         {\{\}, True, ()}
-         {201 \OTWeakarrow {\underline{\texttt{out(m,c)}}\subst{(m\gets \texttt{r1\_msg}, c\gets \texttt{r1\_ec}}} 202}
-         $
+$ WI_8(n) = \openrule
+         {\{\texttt{Q}\mapsto \texttt{q-recv(r1-msg,r1-ec +n)}\}, True, ()}
+         {201 \OTWeakarrow {\underline{\texttt{out(r1-msg,r1-ec +n)}}} 202}
+         \ \forall n\ge 0$
 
@@
 
-%% \TODO{move text below}
-
-%% \begin{property}[Decomposition of weak open transitions] \TODO{TODO}
-%% Let $A$ be the open automaton that is the semantics of a \pNet $P$, and $<J,\mathcal{S},s_0,\WT>$ a weak open automaton derived from $A$.
-%% Suppose we have the following weak open transitions in $\WT$:
-%% \[\openrule
-%%          {
-%%            \set{\gamma_1},\Pred_1,\Post_1   }
-%%          {s \OTWeakarrow {\tau} s_1}
-%% \qquad 
-%% \openrule
-%%          {
-%%            \set{\gamma_2},\Pred_2,\Post_2   }
-%%          {s_1 \OTWeakarrow {\alpha} s_2}
-%% \qquad
-%% \openrule
-%%          {
-%%            \set{\gamma_3},\Pred_3,\Post_3   }
-%%          {s_2 \OTWeakarrow {\tau} s_3}
-%% \]
-%% Then there is ag weak  open transition of the following form in $\WT$:
-%% \[\openrule
-%%          {
-%%            \set{\gamma},\Pred,\Post   }
-%%          {s \OTWeakarrow {\alpha} s_3}
-%% \]
-%% Suppose additionally $\Post_3=({x_k\gets e_k})^{k\in K}$, we have the following
-%% \[
-%% \begin{array}{rcl}
-%% \gamma&=& \gamma_1\dotcup\gamma_2\dotcup\gamma_3\\
-%% \Pred&=&\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}\\
-%% \Post &=& ({x_k\gets ((e_k\subst{\Post_2})\subst{\Post_1})})^{k\in K}
-%% \end{array}\]
-%% \end{property}
-
 \subsection{Properties of weak bisimulation for open pNets}
@@
 \subsection{Running example}
-- In section \ref{def:weakOT} we have shown the full satured weak automaton for both the specification and the implementation of the simple protocol.
-
-\TODO{Je ne pense pas que nous ayons un algo de bisim weak operationnel pour la publi, mais ca n'est pas completement impossible nonp[l;us...
-Au pire, argumenter intuitivement sur papier, en donnat les classes d'equivalence et les predicats.}
-
+In section \ref{def:weakOT} we have shown the full satured weak automaton for both the specification and the implementation of the simple protocol.
+We will show here how we can check if some given relation between these two automata is a weak FH-Bisimulation.
+
+\medskip
+\noindent
+Preliminary remarks:
   \begin{itemize}
-    \item[] Both pNets trivialy verify the ``non-observability''
+    \item Both pNets trivialy verify the ``non-observability''
       condition: the only vectors having $\tau$ as an action of a
       sub-net are of the form ``$< -, \tau, -> -> \tau$''.
+      \item We must take care of variable name conflicts: in our example, the state variables of the 2 systems already have different names, but the action parameters occuring in the transitions (m, msg, ec) are the same, that is not correct.
+In the tools, this is managed by the static semantic layer; in the following example, we have renamed all conflicting variables with 1 for the Spec, and 2 for the Impl.
   \end{itemize}
 
-  Now consider the following triples:
+  Now consider relation $\mathcal{R}$ defined by the following triples:
+
+  \begin{tabular}{|c|c|l|}
+\hline
+    Spec state & Impl state & Predicate\\
+    \hline
+    b0 & $\ostate{000}$ & True\\
+    b0 & $\ostate{202}$ & True\\
+    b1 & $\ostate{100}$ & $\texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec}$\\
+    b1 & $\ostate{210}$ & $\texttt{b1\_msg = m1\_msg} \land \texttt{b1\_ec = m1\_ec}$\\
+    b1 & $\ostate{220}$ & $\texttt{b1\_msg = m2\_msg} \land \texttt{b1\_ec = m2\_ec}$\\
+    b1 & $\ostate{201}$ & $\texttt{b1\_msg = r1\_msg} \land \texttt{b1\_ec = r1\_ec}$\\
+    \hline
+    \end{tabular}
+
+  \medskip
+  Checking that $\mathcal{R}$ is a weak FH-Bisimulation means checking, for each of these triples, that each WOT of one the states corresponds to a set of WOTs of the other, using the conditions from Definition \ref{def-Weak-bisim}.
+  We give here two examples.
+
+  Consider the first triple from the table, and transition $WS_3(n)$ from state $\ostate{b0}$ for some fixed integer $n$. Its easy to guess that it will correspond to $WI_3(n)$ of $\ostate{000}$.
+
+  $ WS_3(n) = \openrule
+  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
+    (\texttt{b1\_msg}\gets \texttt{m}, \texttt{b1\_ec}\gets n)}
+  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
+  $
+
+$ WI_3(n) = \openrule
+  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
+    (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets n)}
+  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
+  $
+
+  Let check formally the conditions:
+
+\begin{itemize}
+  \item Their sets of active (non-silent) holes is the same: $\{P\}$.
+  \item Triple ($\ostate{b1},  \ostate{100},  \texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec}$) is in $\mathcal{R}$.
+  \item The verification condition \\
+    $\Pred \land \Pred_{OT}%\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
+   \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
+     \!\land\! \alpha\!=\!\alpha_x\! \land\!  
+     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}$
+
+\medskip Gives us:
+
+\TODO{Insert here $\forall \phi(m1,m2)$ }
+
+$True \land True\hspace{1cm} \implies\\ 
+\texttt{p-send(m1)} = \texttt{p-send(m2)}
+\land True
+\land \underline{\texttt{in(m1)}} = \underline{\texttt{in(m2)}}
+\land (\texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec})
+\subst{(\texttt{b1\_msg}\gets \texttt{m}, \texttt{b1\_ec}\gets n)
+  \uplus (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets n)}
+$
+
+\medskip That reduces to:
+
+$\forall \texttt{m1}. \exists \texttt{m2}.
+(\texttt{p-send(m1)} = \texttt{p-send(m2)}
+\land \texttt{in(m1)} = \texttt{in(m2)}
+\land \texttt{m}=\texttt{m} \land n=n)$
+
+\medskip That is a tautology.
+
+\end{itemize}
 
@@
 
-$ 3' = \openrule
+$ WI_3(n) = \openrule
   {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
-    (\texttt{m1\_msg}\gets m, \texttt{m1\_ec}\gets n)}
-  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 210}
+    (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets n)}
+  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
   \ \forall n\ge 0$
 
-$ 3'' = \openrule
-  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True, 
-    (\texttt{m2\_ec}\gets n)}
-  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 220}
-  \ \forall n\ge 0$
-
-         $ 4 = \openrule
+$ WI_4(n) = \openrule
          {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n)}
@@
 
-$ 8 = \openrule
-         {\{\}, True, ()}
-         {201 \OTWeakarrow {\underline{\texttt{out(m,c)}}\subst{(m\gets \texttt{r1\_msg}, c\gets \texttt{r1\_ec}}} 202}
-         $
-
+$ WI_8(n) = \openrule
+         {\{\texttt{Q}\mapsto \texttt{q-recv(r1-msg,r1-ec +n)}\}, True, ()}
+         {201 \OTWeakarrow {\underline{\texttt{out(r1-msg,r1-ec +n)}}} 202}
+         \ \forall n\ge 0$
+
+$ WI_9(n) = \openrule
+         {\{\}, True, (\texttt{m1\_ec}\gets \texttt{m1\_ec}+n)}
+         {210 \OTWeakarrow {\tau} 210}
+         \ \forall n\ge 0$
 \end{document}

### 2020-02-24 2016-Weak-FH-Bisim/WeakBisim.tex
work on appendix

--- 2020-02-19 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
-%% \TODO{voisr si on redefinit les bigotimes pour prendre des maps et retourner des maps au lieu des substitutions (et on englobe dans une subst a la fin)}
-
-%% \TODO{prendre soin des posts sur les actions partout}
-
-%% ===> dealine 14 Juillet
-
-%% TODOs du 19 decembre
-
-%% - enlever 5.2 et citer avocs
-
-%% - ajouter des proof sketch dans le papier
-
-%% - def 11 point 2:
-%% A, Pred, Post
-%% -----------   in T
-%% s->s'
-%% et A(j)=tau
-%% implies blablabla
-
-%% OLD OLD OLD (check)
-%% Notes de reunion 24 Sept
-
-%% - etat de l art: il faudrait des refs sur bisim en gemneral, probablement avec pas mal de pi calcul (Eric?), des refs sur pourquoi pnets et des refs sur utilite de la weak bisim en verif
-
-%% - target: JLamp
-
-%% Conventions
-%% [14/9/2018]
-
-%% Dans le texte pas de $\backslash$ devant pNet et pLTS
-
-%% pNet devient P ou Q dans les equations; on garde $pLTS$
-
-%% \medskip
-
-%% TODOS et deadline
-
-%% Global and questions:
-%% \begin{itemize}
-%% \item \TODO{should we use iff/implies or LeftRightArrow/Rightarrow}
-%% \item related works
-%% \end{itemize}
-%% Ludo:
-%% \begin{itemize}
-%% \item[X] reorga sec weak bisim + thm -> 10 Juil
-%% \item[X]  intro et orga globale du papier -> fin aout
-%% \item[partial] explication dans semantique open pnets et composition
-%% \item uniformisation pNet P Q
-%% \end{itemize}
+\TODO{voisr si on redefinit les bigotimes pour prendre des maps et retourner des maps au lieu des substitutions (et on englobe dans une subst a la fin)}
+
+\TODO{prendre soin des posts sur les actions partout}
+
+===> dealine 14 Juillet
+
+TODOs du 19 decembre
+
+- enlever 5.2 et citer avocs
+
+- ajouter des proof sketch dans le papier
+
+- def 11 point 2:
+A, Pred, Post
+-----------   in T
+s->s'
+et A(j)=tau
+implies blablabla
+
+OLD OLD OLD (check)
+Notes de reunion 24 Sept
+
+- etat de l art: il faudrait des refs sur bisim en gemneral, probablement avec pas mal de pi calcul (Eric?), des refs sur pourquoi pnets et des refs sur utilite de la weak bisim en verif
+
+- target: JLamp
+
+Conventions
+[14/9/2018]
+
+Dans le texte pas de $\backslash$ devant pNet et pLTS
+
+pNet devient P ou Q dans les equations; on garde $pLTS$
+
+\medskip
+
+TODOS et deadline
+
+Global and questions:
+\begin{itemize}
+\item \TODO{should we use iff/implies or LeftRightArrow/Rightarrow}
+\item related works
+\end{itemize}
+Ludo:
+\begin{itemize}
+\item[X] reorga sec weak bisim + thm -> 10 Juil
+\item[X]  intro et orga globale du papier -> fin aout
+\item[partial] explication dans semantique open pnets et composition
+\item uniformisation pNet P Q
+\end{itemize}
 
@@
 argument, through the two protocol entities.
-Process $P$ send an $\texttt{p-send(m)}$ message to the $Sender$; this communication is denoted as $\texttt{\underline{in(m)}}$, where underline actions represent internal actions (similar to the $\tau$ of CCS), that cannot be further synchronised with the environment.
+Process $P$ send an $\texttt{p\_send(m)}$ message to the $Sender$; this communication is denoted as $\texttt{\underline{in(m)}}$, where underline actions represent internal actions (similar to the $\tau$ of CCS), that cannot be further synchronised with the environment.
 At the other end process $Q$ receives the message from the $Receiver$.
-The holes $P$ and $Q$ can also have other interactions with their environment, represented here by actions $\texttt{p-a}$ and $\texttt{q-b}$.
+The holes $P$ and $Q$ can also have other interactions with their environment, represented here by actions $\texttt{p\_a}$ and $\texttt{q\_b}$.
 The underlying network is modelled by a medium entity transporting messages from the sender to the receiver, and that is able to detect transport errors, and signal them to the sender.
@@
 Nodes of the tree are synchronized using four synchronization vectors, that  express the possible synchronization between the parameterized actions of a subset of the nodes.
-For instance, in the vector "$< \texttt{p-send(m)},\texttt{in(m)},\_> \rightarrow \texttt{\underline{in(m)}}$ only $P$ and {\it PrefectBuffer} nodes are involved in the synchronization.
-More precisely, the synchronization between these processes occurs when  process $P$  performs $\texttt{p-send(m)}$  action sending a message, and  the medium accepts the message through $\texttt{in(m)}$ action  at the same time.
+For instance, in the vector "$< \texttt{p\_send(m)},\texttt{in(m)},\_> \rightarrow \texttt{\underline{in(m)}}$ only $P$ and {\it PrefectBuffer} nodes are involved in the synchronization.
+More precisely, the synchronization between these processes occurs when  process $P$  performs $\texttt{p\_send(m)}$  action sending a message, and  the medium accepts the message through $\texttt{in(m)}$ action  at the same time.
 And the result that will be returned at upper level is the internal action  $\texttt{\underline{in(m)}}$.
@@
 On the top we show the subset of the original open automaton (from Figure \ref{SimpleProtCounter:SpecOA}) considered here, and at the bottom the generated weak transition.
-The weak open transition shown here is the transition delivering the result of the algorithm to hole $Q$ by applying rules: \WTUn,\WTDeux, and \WTTrois.
+The weak open transition here is the transition delivering the result of the algorithm to hole $Q$ by applying or rules: \WTUn,\WTDeux, and \WTTrois.
 First rule \WTUn~ adds an $\texttt{WT}_\tau$ loop on each state.
@@
   \begin{example}
-    Figures \ref{SimpleProtCounter:WeakSpecOA} and \ref{SimpleProtCounter:ImplOA} respectively show the weak automata of the simple protocol specification and implementation.
+    Figures \ref{SimpleProtCounter:WeakSpecOA} and \ref{SimpleProtCounter:SpecOA-partial} respectively show the weak automata of the simple protocol specification and implementation.
     \TODO{comment...}
-
-    For readability, we did not include the full details of the Implementation weak open transitions in Figure \ref{SimpleProtCounter:ImplOA}, they will appear below.
-In this automaton, many WOT are similar, and numbered accordingly as 3, 3', 3'', and 8, 8', 8'' respectively: they only differ by the name of the state variables in their respective source or target states.
 \end{example}
@@
   \caption{Weak Open Automaton of the implementation}
-   \label{SimpleProtCounter:ImplOA}
+   \label{SimpleProtCounter:SpecOA-partial}
 \end{figure}
+
+%% \TODO{Eric: insert here a table with the details of the WOTs.Il manque encore au moins 3 WOT dans ce dessin...}
+
+%% \smallskip
+%% $1^st$ try, user-friendly style:
+
+%% $$ 3 = \tau^*; \underline{in(m)}\{s1\_c:=0, s1\_m:=m\}; \tau\{s1\_c++\}^*$$
+
+%% \smallskip
+%% $2^nd$ try, full formal style ?:
+%% \medskip
 
@@
 
-$post_3 = (\texttt{s1\_ec}\gets 0, \texttt{s1\_m}\gets \texttt{m})$
-
-$post_4 = (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec})$
-
-$post_5 = (\texttt{m2\_ec}\gets \texttt{m1\_ec})$
-
-$post_6 = (\texttt{s1\_ec}\gets \texttt{m2\_ec+1})$
-
-$post_7 = (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_ec}\gets \texttt{m1\_ec})$
+$post_3 = (\texttt{s1\_c}\gets 0, \texttt{s1\_m}\gets \texttt{m})$
+
+$post_4 = (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_c}\gets \texttt{s1\_c})$
+
+$post_5 = (\texttt{m2\_c}\gets \texttt{m1\_c})$
+
+$post_6 = (\texttt{s1\_c}\gets \texttt{m2\_c+1})$
+
+$post_7 = (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_c}\gets \texttt{m1\_c})$
 
@@
 $Post_{456} = post_6 \shortotimes\ post_5 \shortotimes\ post_4
-= (\texttt{s1\_ec}\gets \texttt{s1\_ec}+1)$.
+= (\texttt{s1\_c}\gets \texttt{s1\_c}+1)$.
 \medskip
 
-So if we denote ${Post_{456}}^*$ any iteration of this loop, we get ${Post_{456}}^* = (\texttt{s1\_ec}\gets \texttt{s1\_ec}+n)$ for any $n\ge 0$, and we will get e.g.
-the Post of the weak OT number 3' as $ post_4\shortotimes {Post_{456}}^*\shortotimes\ post_3 = (\texttt{m1\_msg}\gets m, \texttt{m1\_ec}\gets n), \forall n\ge 0$
+So if we denote ${Post_{456}}^*$ any iteration of this loop, we get ${Post_{456}}^* = (\texttt{s1\_c}\gets \texttt{s1\_c}+n)$ for any $n\ge 0$, and we will get e.g.
+the Post of the weak OT number 3' as $ post_4\shortotimes {Post_{456}}^*\shortotimes\ post_3 = (\texttt{m1\_msg}\gets m, \texttt{m1\_c}\gets n), \forall n\ge 0$
 \medskip
 
-We can now show some of the weak OTs of Figure \ref{SimpleProtCounter:SpecOA-partial} (the full table is included in Appendix \ref{Appendix:FullExample}) :
+We can now show some of the weak OTs of Figure \ref{SimpleProtCounter:SpecOA-partial} (the full table will be included in Appendix \ref{Appendix:FullExample}) :
 \smallskip
@@
 $ 1 = \openrule
-{\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], ()}
+{\{\texttt{P}\mapsto \texttt{p\_a}\}, [\forall \texttt{m}. \texttt{p\_a} \neq \texttt{p\_send(m)} ], ()}
 {000 \OTWeakarrow {\tau} 000}$
 
+$ 2 = \openrule
+{\{\texttt{Q}\mapsto \texttt{q\_b}\}, [\forall \texttt{m}. \texttt{q\_b} \neq \texttt{q\_recv(m)} ], ()}
+{000 \OTWeakarrow {\tau} 000}$
+
+$ 3 = \openrule
+  {\{\texttt{P}\mapsto \texttt{p\_send(m)}\}, True,
+    (\texttt{s1\_msg}\gets m, \texttt{s1\_c}\gets n)}
+  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
+  \ \forall n\ge 0$
+
 $ 3' = \openrule
-  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
-    (\texttt{m1\_msg}\gets m, \texttt{m1\_ec}\gets n)}
+  {\{\texttt{P}\mapsto \texttt{p\_send(m)}\}, True,
+    (\texttt{m1\_msg}\gets m, \texttt{m1\_c}\gets n)}
   {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 210}
@@
 
+$ 3'' = \openrule
+  {\{\texttt{P}\mapsto \texttt{p\_send(m)}\}, True, 
+    (\texttt{m2\_c}\gets n)}
+  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 220}
+  \ \forall n\ge 0$
+
          $ 4 = \openrule
-         {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n)}
+         {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_c}\gets \texttt{s1\_c}+n)}
          {100 \OTWeakarrow {\tau} 210}
@@
 
+$ 5 = \openrule
+         {\{\}, True, (\texttt{m2\_c}\gets \texttt{m1\_c}+n)}
+         {210 \OTWeakarrow {\tau} 220}
+         \ \forall n\ge 0$
+
+$ 6 = \openrule
+         {\{\}, True, (\texttt{s1\_c}\gets \texttt{m2\_c}+n)}
+         {220 \OTWeakarrow {\tau} 100}
+         \ \forall n\ge 0$
+
+$ 7 = \openrule
+         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_c}\gets \texttt{s1\_c}+n)}
+         {100 \OTWeakarrow {\tau} 201}
+         \ \forall n\ge 0$
+
+$ 7' = \openrule
+         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_c}\gets \texttt{m1\_c}+n)}
+         {210 \OTWeakarrow {\tau} 201}
+         \ \forall n\ge 0$
+
+$ 7'' = \openrule
+         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_c}\gets \texttt{m2\_c}+n)}
+         {220 \OTWeakarrow {\tau} 201}
+         \ \forall n\ge 1$
+
 $ 8 = \openrule
          {\{\}, True, ()}
-         {201 \OTWeakarrow {\underline{\texttt{out(m,c)}}\subst{(m\gets \texttt{r1\_msg}, c\gets \texttt{r1\_ec}}} 202}
+         {201 \OTWeakarrow {\underline{\texttt{out(m,c)}}\subst{(m\gets \texttt{r1\_msg}, c\gets \texttt{r1\_c}}} 202}
          $
 
+\newpage
 \subsection{Composition properties: composition of weak open transitions}
@@
 \alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'$; or \\ 
-there exist   $\set{\beta_{1i}}$, $\set{\beta_{2i}}$, and $\set{\beta_{3i}}$, $\Pred_{1i}$, $\Pred_{3i}$, $\Post_{1i}$, and  $\Pred_2$, $\Post_2$ s.t.:
+there exist   $\set{\beta_{1i}}$, $\set{\beta_{2i}}$, and $\set{\beta_{3i}}$, $\Pred_{1i}$, $\Pred_{3i}$, $\Post_{1i}$, and  $\Pred_2$, $\Post_2$ s.t.\footnote{$n=0$ (resp.
+$m=0$) corresponds to the case where there is no $\tau$ transition before (resp.
+after) the transition $\alpha$.}:
 \begin{mathpar}
@@
 %\inferrule 
-\forall i \in [0..n].\openrule
+\forall i \in [1..n].\openrule
     {
@@
 \quad \wedge\\
-\forall i \in [0..m].\openrule
+\forall i \in [1..m].\openrule
          {
@@
 $
-\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n}^{0}\Post_{1j}}}\\
-s=s_{10} \wedge s_{1(n+1)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
+\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n}^{1}\Post_{1j}}}\\
+s=s_{11} \wedge s_{1(n+1)}=s_2 \wedge s'_2 = s_{31} \wedge s_{3(m+1)}=s'\\
 \displaystyle{
-\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup}\\
-~\qquad \displaystyle{\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
+\set{\gamma}=\mybigdotcup_{i=1}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{1}\Post_{1j}}} \dotcup}\\
+~\qquad \displaystyle{\mybigdotcup_{i=1}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{1}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{1}\Post_{1j}} }}
 \\
-\Pred=\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=n}^{0}\Post_{1j}}\land\\ 
-~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}}\Big)\\
-\Post=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}
+\Pred=\bigwedge_{i=1}^n\Pred_{1i}\subst{\bigotimes_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=n}^{1}\Post_{1j}}\land\\ 
+~\qquad\quad\Big(\bigwedge_{i=1}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{1}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{1}\Post_{1j}}\Big)\\
+\Post=\bigotimes_{j=m}^{1}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{1}\Post_{1j}
 $
@@
 \begin{itemize}
-\item The base case there is one transition, so $n=0$ and $m=0$, we have:
+\item In the base case there is one transition, which corresponds to $n=0$ and $m=0$, we have:
 \begin{mathpar}
@@
 \end{mathpar} 
-by rule \WTDeux we can directly conclude the implication: 
+by rule \WTDeux\ we can directly conclude the implication: 
  \begin{mathpar}
@@
 Induction step is to infer that formula holds for transitions of length $m+1$ or $n+1$.
-We consider the case $n'=n+1$ (because $m'=m+1$ is similar).
+We consider the case $n'=n+1$ ($m'=m+1$ is similar).
 We want to prove (1) $\Rightarrow$ (2) in the lemma, and in (1) we  focus on the case where there is a set of open transitions (this is the case: $s\neq s'$).
@@
 \begin{mathpar}
-\Big(\forall i \in [0..n+1].\openrule
+\Big(\forall i \in [1..n+1].\openrule
     {
@@
 \quad \wedge\\
-~~\qquad\qquad\forall i \in [0..m].\openrule
+~~\qquad\qquad\forall i \in [1..m].\openrule
          {
@@
 
-By recurrence hypothesis we suppose that the (1) $\Rightarrow$ (2) holds for $n$ and $m$ (compared to the line above, we remove the first $\tau$ transition). We have:\\
+By recurrence hypothesis we suppose that  (1) $\Rightarrow$ (2) holds for $n$ and $m$ (compared to the line above, we remove the first $\tau$ transition). We have:\\
 
@@
 %\inferrule 
-\Big(\forall i \in [1..n+1].\openrule
+\Big(\forall i \in [2..n+1].\openrule
     {
@@
 \, \wedge\\
-~~\hspace{2.25cm}\forall i \in [0..m].\openrule
+{}~~\hspace{2.25cm}\forall i \in [1..m].\openrule
          {
@@
 $
-\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\!\!\Post_{1j}}}\\
-s''=s_{10} \wedge s_{1(n+2)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
+\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{2}\!\!\Post_{1j}}}\\
+s''=s_{12} \wedge s_{1(n+2)}=s_2 \wedge s'_2 = s_{31} \wedge s_{3(m+1)}=s'\\
 \displaystyle{
-\set{\gamma}=\mybigdotcup_{i=1}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup}\\
-~\qquad \displaystyle{\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
+\set{\gamma}=\mybigdotcup_{i=2}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{2}\Post_{1j}}} \dotcup}
 \\
-\Pred=\bigwedge_{i=1}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{1}\Post_{1j}}\land\\ 
-~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}}\Big)\\
-\Post=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}
+{}~\qquad 
+\displaystyle{\mybigdotcup_{i=1}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{1}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{2}\Post_{1j}} }}
+\\
+\Pred=\bigwedge_{i=2}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{2}\Post_{1j}}\land
+\\ 
+{}~\qquad\quad
+\Big(\bigwedge_{i=1}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{1}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{2}\Post_{1j}}\Big)\\
+\Post=\bigotimes_{j=m}^{1}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{2}\Post_{1j}
 $
@@
          {
-           \set{\beta_{10}},\Pred_{10},\Post_{10}}
-         {s_{10} \OTarrow {\tau} s_{11}} \in \mathcal{T}%}
+           \set{\beta_{11}},\Pred_{11},\Post_{11}}
+         {s_{11} \OTarrow {\tau} s_{12}} \in \mathcal{T}%}
 \end{mathpar}
@@
          {
-           \set{\beta_{10}},\Pred_{10},\Post_{10}}
-         {s_{10} \OTarrow {\tau} s_{11}} \in \mathcal{T}
+           \set{\beta_{11}},\Pred_{11},\Post_{11}}
+         {s_{11} \OTarrow {\tau} s_{12}} \in \mathcal{T}
 \Rightarrow 
@@
        {
-           \vis{\set{\beta_{10}}}\!,\Pred_{10},\Post_{10}
-				 } {s_{10} \OTWeakarrow {\tau}s_{11}} \in \WT
+           \vis{\set{\beta_{11}}}\!,\Pred_{11},\Post_{11}
+				 } {s_{11} \OTWeakarrow {\tau}s_{12}} \in \WT
 }
@@
        {
-           \vis{\set{\beta_{10}}}\!,\Pred_{10},\Post_{10}
-				 } {s_{10} \OTWeakarrow {\tau}s_{11}}\! \in\! \WT
+           \vis{\set{\beta_{11}}}\!,\Pred_{11},\Post_{11}
+				 } {s_{11} \OTWeakarrow {\tau}s_{12}}\! \in\! \WT
 \quad
@@
 \\
-\set{\gamma''}= \vis{\set{\beta_{10}}} \dotcup \set{\gamma}\subst{\Post_{10}}\quad
-\Pred\,''=\Pred_{10}\land\Pred\subst{\Post_{10}}\\%\land (\Pred_3\subst{\Post_2})\subst{\Post_{10}}
-\Post\,''=\Id(s'')\shortotimes\Post\shortotimes\Post_{10} \quad \alpha''=\alpha'\subst{\Post_{10}}
+\set{\gamma''}= \vis{\set{\beta_{11}}} \dotcup \set{\gamma}\subst{\Post_{11}}\quad
+\Pred\,''=\Pred_{11}\land\Pred\subst{\Post_{11}}\\%\land (\Pred_3\subst{\Post_2})\subst{\Post_{11}}
+\Post\,''=\Id(s'')\shortotimes\Post\shortotimes\Post_{11} \quad \alpha''=\alpha'\subst{\Post_{11}}
 }
@@
 				 } 
-         {s_{10} \OTWeakarrow {\alpha''} s'} \in\!\WT
+         {s_{11} \OTWeakarrow {\alpha''} s'} \in\!\WT
 } \WTTrois
@@
 \alpha''=\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}}\subst{\Post_{10}} = \alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{0}\Post_{1j}}}\\
-s_{10}=s_{10} \wedge s_{1(n+2)}=s_{2} \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
+s_{11}=s_{11} \wedge s_{1(n+2)}=s_{2} \wedge s'_2 = s_{31} \wedge s_{3(m+1)}=s'\\
 \displaystyle{
-\set{\gamma''}=\mybigdotcup_{i=0}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup}\\
-~\qquad~\displaystyle{ \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
+\set{\gamma''}=\mybigdotcup_{i=1}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup}\\
+{}~\qquad~\displaystyle{ \mybigdotcup_{i=1}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{1}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
 \\
-\Pred=\bigwedge_{i=0}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{0}\Post_{1j}}\land\\ 
-~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{0}\Post_{1j}}\Big)\\
-\Post=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{0}\Post_{1j}
+\Pred=\bigwedge_{i=1}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{1}\Post_{1j}}\land\\ 
+{}~\qquad\quad\Big(\bigwedge_{i=1}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{1}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}}\Big)\\
+\Post=\bigotimes_{j=m}^{1}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}
 $
@@
 \]
-with \\
-
+with 
 $\set{\gamma'_{1p}}=\set{\vis{\beta_{1p}}}, \Pred\,'_{1p}=\Pred_{1p}, \Post\,'_{1p}=\Post_{1p}$\\
@@
 
-We now have to compare each element of the obtained WOT with the conclusion of the lemma:
+We now  compare each element of the obtained WOT with the conclusion of the lemma:
 \begin{align*}
@@
 First suppose $j\in J\setminus\{j_0\}$ we have $\gamma'_j=\gamma_j$ because $\Post'_{ij}$ has no effect on variables of $P$ and on $\beta_{1pj}$, consequently\\
-
-$\displaystyle{\gamma'_j=\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \dotcup  \vis{{\beta_{2j}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}\, \dotcup}\\
-~\qquad\qquad \displaystyle{\mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}}
-$
+\begin{equation*}
+\begin{split}\gamma'_j=&\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \dotcup  \vis{{\beta_{2j}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}\, \dotcup\\
+&
+\mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}
+\end{split}
+\end{equation*}
 
@@
 giving the exact indices is cumbersome because Post'ij is either empty or postij for the same indices as gamma, this can also be related with the ni and n'i}
-We obtain:\\
-
-$\displaystyle{\gamma'_j =
-\mybigdotcup_{i=0}^{m_1}{\gamma'_{1ij}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{1k}}\dotcup
- {\gamma'_{2 j}}\subst{\bigotimes_{k=m_1}^{0}\Post\,'_{1k}}\,\dotcup}$\\
-$~\qquad \qquad\displaystyle{ \mybigdotcup_{i=0}^{m_2}{\gamma'_{3ij}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}}$\\
-$~\qquad \quad\displaystyle{\mybigdotcup_{t=0}^{n} {\gamma_{tj}}\subst{\bigotimes_{k=t-1}^{0} \Post_{k}}}$
-
-Concerning predicates, we also separate predicates on $P$ from predicates on $Q$, and from the equality on the action filling the hole:\\
-\begin{small}
-$
-\displaystyle{\Pred\,''=\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land}$\\
-$~\qquad\qquad\displaystyle{\bigwedge_{i=0}^{m_3}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}}$\\
-$~\qquad\quad=\displaystyle{\big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land}$\\
-$~\qquad\qquad\,\displaystyle{\bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\big) \land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i \land}$\\
-%$~\qquad\qquad\,\displaystyle{\bigwedge_{i=0}^{m-1}(\beta_{1{n_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j={n_i}-1}^{0}\Post\,'_{1j}}\land(\beta_{2{j_0}}=\alpha_m) \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land}$\\
-%$~\qquad\qquad\,\displaystyle{\bigwedge_{i=m+1}^{n}(\beta_{3{n'_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j=n'_i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\Big)}$\\
-\end{small}
-%%%%%%% Je suis ici!!!!!
-
-\begin{small}
+We obtain:
 \begin{equation*}
 \begin{split}
-\Pred''&=\Big(\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\ &\qquad
+\gamma'_j =&
+\mybigdotcup_{i=0}^{m_1}{\gamma'_{1ij}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{1k}}\dotcup
+ {\gamma'_{2 j}}\subst{\bigotimes_{k=m_1}^{0}\Post\,'_{1k}}\,\dotcup\\
+& \mybigdotcup_{i=0}^{m_2}{\gamma'_{3ij}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}~\dotcup~
+{\mybigdotcup_{t=0}^{n} {\gamma_{tj}}\subst{\bigotimes_{k=t-1}^{0} \Post_{k}}}   
+\end{split}
+\end{equation*}
+
+Concerning predicates, we also separate predicates on $P$ from predicates on $Q$, and from the equality on the action filling the hole:\\
+%\begin{small}
+%\begin{equation*}
+%\begin{split}
+%\Pred\,''&=\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\
+%&~~{\bigwedge_{i=0}^{m_3}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}}\\
+%&=\big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\
+%&~~~\bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\big) \land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i \land
+%%$~\qquad\qquad\,\displaystyle{\bigwedge_{i=0}^{m-1}(\beta_{1{n_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j={n_i}-1}^{0}\Post\,'_{1j}}\land(\beta_{2{j_0}}=\alpha_m) \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land}
+%\end{split}
+%\end{equation*}
+%%$~\qquad\qquad\,\displaystyle{\bigwedge_{i=m+1}^{n}(\beta_{3{n'_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j=n'_i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\Big)}$\\
+%\end{small}
+
+\begin{footnotesize}
+\begin{equation*}
+\begin{split}
+\Pred\,''&=\Big(\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\ &\qquad
 ~\quad\bigwedge_{i=0}^{m_3}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\Big)\\
@@
 \end{equation*}
-\end{small}
+\end{footnotesize}
 
@@
 state a0
-transition m_recv(msg,c) -> a1 {a1_msg:=msg, a1_ec:=c}
+transition m_recv(msg,c) -> a1 {a1_msg:=msg, a1_c:=c}
 
 state a1
-vars a1_msg:Data a1_ec:Int
-transition m_send(a1_msg, a1_ec) -> a0 
+vars a1_msg:Data a1_c:Int
+transition m_send(a1_msg, a1_c) -> a0 
 transition synchro($tau) -> a2
@@
 state s0
-transition s_recv(msg) -> s1 {s1_msg:=msg, s1_ec:=0}
+transition s_recv(msg) -> s1 {s1_msg:=msg, s1_c:=0}
 
 state s1
-vars s1_msg:Data s1_ec:Int
-transition s_send(s1_msg, s1_ec) -> s2 {s2_ec:=s1_ec}
+vars s1_msg:Data s1_c:Int
+transition s_send(s1_msg, s1_c) -> s2 {s2_c:=s1_c}
 
 state s2
-vars  s2_ec:Int
+vars  s2_c:Int
 transition $s_ack -> s0
-transition $s_error -> s1 {s1_ec:=s2_ec+1}
+transition $s_error -> s1 {s1_c:=s2_c+1}
 
@@
 state r0
-transition r_recv(msg,c) -> r1 {r1_msg:=msg, r1_ec:=c}
+transition r_recv(msg,c) -> r1 {r1_msg:=msg, r1_c:=c}
 
 state r1
-vars r1_msg:Data r1_ec:Int
-transition r_send(r1_msg, r1_ec) -> r2
+vars r1_msg:Data r1_c:Int
+transition r_send(r1_msg, r1_c) -> r2
 
@@
 %% - pLTS: Sender
-%% - - Transition: s0---in(msg)-->s1, { s1_msg := msg s1_ec := 0}
-%% - - Transition: s1---s_send(s1_msg, s1_ec)-->s2, {}
+%% - - Transition: s0---in(msg)-->s1, { s1_msg := msg s1_c := 0}
+%% - - Transition: s1---s_send(s1_msg, s1_c)-->s2, {}
 %% - - Transition: s2---s_ack-->s0, {}
-%% - - Transition: s2---s_error-->s1, { s1_ec := s2_ec+1}
-%% - - Variable: s1_ec, State: s1, Value(s) = 0,s2_ec+1,
+%% - - Transition: s2---s_error-->s1, { s1_c := s2_c+1}
+%% - - Variable: s1_c, State: s1, Value(s) = 0,s2_c+1,
 %% - - Variable: s1_msg, State: s1, Value(s) = msg,
 %% - pLTS: M1
-%% - - Transition: a0---m_recv(msg, c)-->a1, { a1_msg := msg a1_ec := c}
-%% - - Transition: a1---m_send(a1_msg, a1_ec)-->a0, {}
+%% - - Transition: a0---m_recv(msg, c)-->a1, { a1_msg := msg a1_c := c}
+%% - - Transition: a1---m_send(a1_msg, a1_c)-->a0, {}
 %% - - Transition: a1---_tau_-->a2, {}
@@
 %% - - Variable: a1_msg, State: a1, Value(s) = msg,
-%% - - Variable: a1_ec, State: a1, Value(s) = c,
+%% - - Variable: a1_c, State: a1, Value(s) = c,
 %% - pLTS: Receiver
-%% - - Transition: r0---r_recv(msg, c)-->r1, { r1_msg := msg r1_ec := c}
-%% - - Transition: r1---out(r1_msg, r1_ec)-->r2, {}
+%% - - Transition: r0---r_recv(msg, c)-->r1, { r1_msg := msg r1_c := c}
+%% - - Transition: r1---out(r1_msg, r1_c)-->r2, {}
 %% - - Transition: r2---r_ack-->r0, {}
 %% - - Variable: r1_msg, State: r1, Value(s) = msg,
-%% - - Variable: r1_ec, State: r1, Value(s) = c,
+%% - - Variable: r1_c, State: r1, Value(s) = c,
 %% Holes: Q
@@
 {P|->p_send(m:SV6:1:1)},
-[(msg=m:SV0:12:1)/\((s_recv(msg))=(s_recv(m:SV0:12:1)))], {s1_msg := msg, s1_ec := 0}
+[(msg=m:SV0:12:1)/\((s_recv(msg))=(s_recv(m:SV0:12:1)))], {s1_msg := msg, s1_c := 0}
 	OT:1 ------------------------------------------------------------
@@
 
-{},   [(s1_msg=m:SV1:114:2)/\(s1_ec=c:SV1:114:2)
-  /\((s_send(s1_msg, s1_ec))=(s_send(m:SV1:114:2, c:SV1:114:2)))
+{},   [(s1_msg=m:SV1:114:2)/\(s1_c=c:SV1:114:2)
+  /\((s_send(s1_msg, s1_c))=(s_send(m:SV1:114:2, c:SV1:114:2)))
   /\(msg=m:SV1:114:2)/\(c=c:SV1:114:2)
   /\((m_recv(msg, c))=(m_recv(m:SV1:114:2, c:SV1:114:2)))],
-{s2_ec := s1_ec, a1_msg := msg, a1_ec := c}
+{s2_c := s1_c, a1_msg := msg, a1_c := c}
 	OT:6 ------------------------------------------------------------
@@
 
-{},   [(a1_msg=m:SV2:114:3)/\(a1_ec=c:SV2:114:3)
-  /\((m_send(a1_msg, a1_ec))=(m_send(m:SV2:114:3, c:SV2:114:3)))
+{},   [(a1_msg=m:SV2:114:3)/\(a1_c=c:SV2:114:3)
+  /\((m_send(a1_msg, a1_c))=(m_send(m:SV2:114:3, c:SV2:114:3)))
   /\(msg=m:SV2:114:3)/\(c=c:SV2:114:3)
   /\((r_recv(msg, c))=(r_recv(m:SV2:114:3, c:SV2:114:3)))],
-{r1_msg := msg, r1_ec := c}
+{r1_msg := msg, r1_c := c}
 	OT:9 ------------------------------------------------------------
@@
 {Q|->q_recv(m:SV8:1:3, c:SV8:1:3)},
-[(r1_msg=m:SV5:18:6)/\(r1_ec=c:SV5:18:6)
-  /\((r_send(r1_msg, r1_ec))=(r_send(m:SV5:18:6, c:SV5:18:6)))],   {}
+[(r1_msg=m:SV5:18:6)/\(r1_c=c:SV5:18:6)
+  /\((r_send(r1_msg, r1_c))=(r_send(m:SV5:18:6, c:SV5:18:6)))],   {}
 	OT:12 ------------------------------------------------------------
@@
 
-		{},   [],   {s1_ec := s2_ec+1}
+		{},   [],   {s1_c := s2_c+1}
 	OT:16 --------------------------------------
@@
 ===================
-pLTS States: <s1 vars: { s1_msg <-{msg} s1_ec <-{0, s2_ec+1}}> <a0 vars: {}> <r0 vars: {}>
+pLTS States: <s1 vars: { s1_msg <-{msg} s1_c <-{0, s2_c+1}}> <a0 vars: {}> <r0 vars: {}>
 
@@
 ===================
-pLTS States: <s2 vars: { s2_ec <-{s1_ec}}> <a1 vars: { a1_msg <-{msg} a1_ec <-{c}}> <r0 vars: {}>
+pLTS States: <s2 vars: { s2_c <-{s1_c}}> <a1 vars: { a1_msg <-{msg} a1_c <-{c}}> <r0 vars: {}>
 
@@
 ===================
-pLTS States: <s2 vars: { s2_ec <-{s1_ec}}> <a0 vars: {}> <r1 vars: { r1_ec <-{c} r1_msg <-{msg}}>
+pLTS States: <s2 vars: { s2_c <-{s1_c}}> <a0 vars: {}> <r1 vars: { r1_c <-{c} r1_msg <-{msg}}>
 
@@
 ===================
-pLTS States: <s2 vars: { s2_ec <-{s1_ec}}> <a2 vars: {}> <r0 vars: {}>
+pLTS States: <s2 vars: { s2_c <-{s1_c}}> <a2 vars: {}> <r0 vars: {}>
 
@@
 ===================
-pLTS States: <s2 vars: { s2_ec <-{s1_ec}}> <a0 vars: {}> <r2 vars: {}>
+pLTS States: <s2 vars: { s2_c <-{s1_c}}> <a0 vars: {}> <r2 vars: {}>
 
@@
 %%<s2\_a0\_r0>, encoding the loop.
-
-\begin{figure}[h]
-   \centerline{\includegraphics[width=9cm]{XFIG/SimpleProtImpl-WOA}}
-  \caption{Weak Open Automaton of the implementation}
-   \label{Appendix:SpecOA-partial}
-\end{figure}
-
-In Figure \ref{Appendix:SpecOA-partial} we show the weak oepn automaton of our implementation pNet. Details of the weak transitions is listed here:
-
-$ 1 = \openrule
-{\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], ()}
-{000 \OTWeakarrow {\tau} 000}$
-
-$ 2 = \openrule
-{\{\texttt{Q}\mapsto \texttt{q-b}\}, [\forall \texttt{m}. \texttt{q-b} \neq \texttt{q-recv(m)} ], ()}
-{000 \OTWeakarrow {\tau} 000}$
-
-$ 3 = \openrule
-  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
-    (\texttt{s1\_msg}\gets m, \texttt{s1\_ec}\gets n)}
-  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
-  \ \forall n\ge 0$
-
-$ 3' = \openrule
-  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
-    (\texttt{m1\_msg}\gets m, \texttt{m1\_ec}\gets n)}
-  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 210}
-  \ \forall n\ge 0$
-
-$ 3'' = \openrule
-  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True, 
-    (\texttt{m2\_ec}\gets n)}
-  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 220}
-  \ \forall n\ge 0$
-
-         $ 4 = \openrule
-         {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n)}
-         {100 \OTWeakarrow {\tau} 210}
-         \ \forall n\ge 0$
-
-$ 5 = \openrule
-         {\{\}, True, (\texttt{m2\_ec}\gets \texttt{m1\_ec}+n)}
-         {210 \OTWeakarrow {\tau} 220}
-         \ \forall n\ge 0$
-
-$ 6 = \openrule
-         {\{\}, True, (\texttt{s1\_ec}\gets \texttt{m2\_ec}+n)}
-         {220 \OTWeakarrow {\tau} 100}
-         \ \forall n\ge 0$
-
-$ 7 = \openrule
-         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s1\_ec}+n)}
-         {100 \OTWeakarrow {\tau} 201}
-         \ \forall n\ge 0$
-
-$ 7' = \openrule
-         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_ec}\gets \texttt{m1\_ec}+n)}
-         {210 \OTWeakarrow {\tau} 201}
-         \ \forall n\ge 0$
-
-$ 7'' = \openrule
-         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_ec}\gets \texttt{m2\_ec}+n)}
-         {220 \OTWeakarrow {\tau} 201}
-         \ \forall n\ge 1$
-
-$ 8 = \openrule
-         {\{\}, True, ()}
-         {201 \OTWeakarrow {\underline{\texttt{out(m,c)}}\subst{(m\gets \texttt{r1\_msg}, c\gets \texttt{r1\_ec}}} 202}
-         $
 

### 2020-02-25 2016-Weak-FH-Bisim/WeakBisim.tex
modifs

--- 2020-02-21 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
-    \TODO{introduce the notation for parametrized OTs}
-
     For readability, we did not include the full details of the Implementation weak open transitions in Figure \ref{SimpleProtCounter:ImplOA}, they will appear below.
@@
 \subsection{Running example}
-In section \ref{def:weakOT} we have shown the full satured weak automaton for both the specification and the implementation of the simple protocol.
-We will show here how we can check if some given relation between these two automata is a weak FH-Bisimulation.
-
-\medskip
-\noindent
-Preliminary remarks:
+- In section \ref{def:weakOT} we have shown the full satured weak automaton for both the specification and the implementation of the simple protocol.
+
+\TODO{Je ne pense pas que nous ayons un algo de bisim weak operationnel pour la publi, mais ca n'est pas completement impossible nonp[l;us...
+Au pire, argumenter intuitivement sur papier, en donnat les classes d'equivalence et les predicats.}
+
   \begin{itemize}
-    \item Both pNets trivialy verify the ``non-observability''
+    \item[] Both pNets trivialy verify the ``non-observability''
       condition: the only vectors having $\tau$ as an action of a
       sub-net are of the form ``$< -, \tau, -> -> \tau$''.
-      \item We must take care of variable name conflicts: in our example, the state variables of the 2 systems already have different names, but the action parameters occuring in the transitions (m, msg, ec) are the same, that is not correct.
-In the tools, this is managed by the static semantic layer; in the following example, we have renamed all conflicting variables with 1 for the Spec, and 2 for the Impl.
   \end{itemize}
 
-  Now consider relation $\mathcal{R}$ defined by the following triples:
-
-  \begin{tabular}{|c|c|l|}
-\hline
-    Spec state & Impl state & Predicate\\
-    \hline
-    b0 & $\ostate{000}$ & True\\
-    b0 & $\ostate{202}$ & True\\
-    b1 & $\ostate{100}$ & $\texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec}$\\
-    b1 & $\ostate{210}$ & $\texttt{b1\_msg = m1\_msg} \land \texttt{b1\_ec = m1\_ec}$\\
-    b1 & $\ostate{220}$ & $\texttt{b1\_msg = m2\_msg} \land \texttt{b1\_ec = m2\_ec}$\\
-    b1 & $\ostate{201}$ & $\texttt{b1\_msg = r1\_msg} \land \texttt{b1\_ec = r1\_ec}$\\
-    \hline
-    \end{tabular}
-
-  \medskip
-  Checking that $\mathcal{R}$ is a weak FH-Bisimulation means checking, for each of these triples, that each WOT of one the states corresponds to a set of WOTs of the other, using the conditions from Definition \ref{def-Weak-bisim}.
-  We give here two examples.
-
-  Consider the first triple from the table, and transition $WS_3(n)$ from state $\ostate{b0}$ for some fixed integer $n$. Its easy to guess that it will correspond to $WI_3(n)$ of $\ostate{000}$.
-
-  $ WS_3(n) = \openrule
-  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
-    (\texttt{b1\_msg}\gets \texttt{m}, \texttt{b1\_ec}\gets n)}
-  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
-  $
-
-$ WI_3(n) = \openrule
-  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
-    (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets n)}
-  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
-  $
-
-  Let check formally the conditions:
-
-\begin{itemize}
-  \item Their sets of active (non-silent) holes is the same: $\{P\}$.
-  \item Triple ($\ostate{b1},  \ostate{100},  \texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec}$) is in $\mathcal{R}$.
-  \item The verification condition \\
-    $\Pred \land \Pred_{OT}%\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
-   \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
-     \!\land\! \alpha\!=\!\alpha_x\! \land\!  
-     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}$
-
-\medskip Gives us:
-
-\TODO{Insert here $\forall \phi(m1,m2)$ }
-
-$True \land True\hspace{1cm} \implies\\ 
-\texttt{p-send(m1)} = \texttt{p-send(m2)}
-\land True
-\land \underline{\texttt{in(m1)}} = \underline{\texttt{in(m2)}}
-\land (\texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec})
-\subst{(\texttt{b1\_msg}\gets \texttt{m}, \texttt{b1\_ec}\gets n)
-  \uplus (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets n)}
-$
-
-\medskip That reduces to:
-
-$\forall \texttt{m1}. \exists \texttt{m2}.
-(\texttt{p-send(m1)} = \texttt{p-send(m2)}
-\land \texttt{in(m1)} = \texttt{in(m2)}
-\land \texttt{m}=\texttt{m} \land n=n)$
-
-\medskip That is a tautology.
-
-\end{itemize}
+  Now consider the following triples:
 

### 2020-02-25 2016-Weak-FH-Bisim/WeakBisim.tex
appendix proofs

@@
 \alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'$; or \\ 
-there exist   $\set{\beta_{1i}}$, $\set{\beta_{2i}}$, and $\set{\beta_{3i}}$, $\Pred_{1i}$, $\Pred_{3i}$, $\Post_{1i}$, and  $\Pred_2$, $\Post_2$ s.t.\footnote{$n=0$ (resp.
-$m=0$) corresponds to the case where there is no $\tau$ transition before (resp.
+there exist   $\set{\beta_{1i}}$, $\set{\beta_{2i}}$, and $\set{\beta_{3i}}$, $\Pred_{1i}$, $\Pred_{3i}$, $\Post_{1i}$, and  $\Pred_2$, $\Post_2$, $n\geq -1$, $m\geq -1$ s.t.\footnote{$n=-1$ (resp.
+$m=-1$) corresponds to the case where there is no $\tau$ transition before (resp.
 after) the transition $\alpha$.}:
+
 \begin{mathpar}
@@
 %\inferrule 
-\forall i \in [1..n].\openrule
+\forall i \in [0..n].\openrule
     {
@@
 \quad \wedge\\
-\forall i \in [1..m].\openrule
+\forall i \in [0..m].\openrule
          {
@@
 $
-\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n}^{1}\Post_{1j}}}\\
-s=s_{11} \wedge s_{1(n+1)}=s_2 \wedge s'_2 = s_{31} \wedge s_{3(m+1)}=s'\\
+\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n}^{0}\Post_{1j}}}\\
+s=s_{10} \wedge s_{1(n+1)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
 \displaystyle{
-\set{\gamma}=\mybigdotcup_{i=1}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{1}\Post_{1j}}} \dotcup}\\
-~\qquad \displaystyle{\mybigdotcup_{i=1}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{1}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{1}\Post_{1j}} }}
+\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup}\\
+{}~\qquad \displaystyle{\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
 \\
-\Pred=\bigwedge_{i=1}^n\Pred_{1i}\subst{\bigotimes_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=n}^{1}\Post_{1j}}\land\\ 
-~\qquad\quad\Big(\bigwedge_{i=1}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{1}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{1}\Post_{1j}}\Big)\\
-\Post=\bigotimes_{j=m}^{1}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{1}\Post_{1j}
+\Pred=\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=n}^{0}\Post_{1j}}\land\\ 
+{}~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}}\Big)\\
+\Post=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}
 $
@@
 \begin{itemize}
-\item In the base case there is one transition, which corresponds to $n=0$ and $m=0$, we have:
+\item The base case there is one transition, so $n=-1$ and $m=-1$, we have:
 \begin{mathpar}
@@
 Induction step is to infer that formula holds for transitions of length $m+1$ or $n+1$.
-We consider the case $n'=n+1$ ($m'=m+1$ is similar).
+We consider the case $n'=n+1$ (because $m'=m+1$ is similar).
 We want to prove (1) $\Rightarrow$ (2) in the lemma, and in (1) we  focus on the case where there is a set of open transitions (this is the case: $s\neq s'$).
-In other words, we consider the sequence of ($n+m+2$) open transitions:
-\begin{mathpar}
-\Big(\forall i \in [1..n+1].\openrule
+In other words, we consider the sequence of ($n+m+4$) open transitions:
+\begin{mathpar}
+\Big(\forall i \in [0..n+1].\openrule
     {
@@
 \quad \wedge\\
-~~\qquad\qquad\forall i \in [1..m].\openrule
+~~\qquad\qquad\forall i \in [0..m].\openrule
          {
@@
 %\inferrule 
-\Big(\forall i \in [2..n+1].\openrule
+\Big(\forall i \in [1..n+1].\openrule
     {
@@
 \, \wedge\\
-{}~~\hspace{2.25cm}\forall i \in [1..m].\openrule
+{}~~\hspace{2.25cm}\forall i \in [0..m].\openrule
          {
@@
 $
-\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{2}\!\!\Post_{1j}}}\\
-s''=s_{12} \wedge s_{1(n+2)}=s_2 \wedge s'_2 = s_{31} \wedge s_{3(m+1)}=s'\\
+\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\!\!\Post_{1j}}}\\
+s''=s_{10} \wedge s_{1(n+2)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
 \displaystyle{
-\set{\gamma}=\mybigdotcup_{i=2}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{2}\Post_{1j}}} \dotcup}
+\set{\gamma}=\mybigdotcup_{i=1}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup}\\
+{}~\qquad \displaystyle{\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
 \\
-{}~\qquad 
-\displaystyle{\mybigdotcup_{i=1}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{1}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{2}\Post_{1j}} }}
-\\
-\Pred=\bigwedge_{i=2}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{2}\Post_{1j}}\land
-\\ 
-{}~\qquad\quad
-\Big(\bigwedge_{i=1}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{1}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{2}\Post_{1j}}\Big)\\
-\Post=\bigotimes_{j=m}^{1}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{2}\Post_{1j}
+\Pred=\bigwedge_{i=1}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{1}\Post_{1j}}\land\\ 
+{}~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}}\Big)\\
+\Post=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}
 $
@@
          {
-           \set{\beta_{11}},\Pred_{11},\Post_{11}}
-         {s_{11} \OTarrow {\tau} s_{12}} \in \mathcal{T}%}
+           \set{\beta_{10}},\Pred_{10},\Post_{10}}
+         {s_{10} \OTarrow {\tau} s_{11}} \in \mathcal{T}%}
 \end{mathpar}
@@
          {
-           \set{\beta_{11}},\Pred_{11},\Post_{11}}
-         {s_{11} \OTarrow {\tau} s_{12}} \in \mathcal{T}
+           \set{\beta_{10}},\Pred_{10},\Post_{10}}
+         {s_{10} \OTarrow {\tau} s_{11}} \in \mathcal{T}
 \Rightarrow 
@@
        {
-           \vis{\set{\beta_{11}}}\!,\Pred_{11},\Post_{11}
-				 } {s_{11} \OTWeakarrow {\tau}s_{12}} \in \WT
+           \vis{\set{\beta_{10}}}\!,\Pred_{10},\Post_{10}
+				 } {s_{10} \OTWeakarrow {\tau}s_{11}} \in \WT
 }
@@
        {
-           \vis{\set{\beta_{11}}}\!,\Pred_{11},\Post_{11}
-				 } {s_{11} \OTWeakarrow {\tau}s_{12}}\! \in\! \WT
+           \vis{\set{\beta_{10}}}\!,\Pred_{10},\Post_{10}
+				 } {s_{10} \OTWeakarrow {\tau}s_{11}}\! \in\! \WT
 \quad
@@
 \\
-\set{\gamma''}= \vis{\set{\beta_{11}}} \dotcup \set{\gamma}\subst{\Post_{11}}\quad
-\Pred\,''=\Pred_{11}\land\Pred\subst{\Post_{11}}\\%\land (\Pred_3\subst{\Post_2})\subst{\Post_{11}}
-\Post\,''=\Id(s'')\shortotimes\Post\shortotimes\Post_{11} \quad \alpha''=\alpha'\subst{\Post_{11}}
+\set{\gamma''}= \vis{\set{\beta_{10}}} \dotcup \set{\gamma}\subst{\Post_{10}}\quad
+\Pred\,''=\Pred_{10}\land\Pred\subst{\Post_{10}}\\%\land (\Pred_3\subst{\Post_2})\subst{\Post_{10}}
+\Post\,''=\Id(s'')\shortotimes\Post\shortotimes\Post_{10} \quad \alpha''=\alpha'\subst{\Post_{10}}
 }
@@
 				 } 
-         {s_{11} \OTWeakarrow {\alpha''} s'} \in\!\WT
+         {s_{10} \OTWeakarrow {\alpha''} s'} \in\!\WT
 } \WTTrois
 \end{mathpar}
-where we obtain the conclusion of the lemma, as required with the following assertions (derived from previous assertions):\\
-$
-\alpha''=\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}}\subst{\Post_{10}} = \alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{0}\Post_{1j}}}\\
-s_{11}=s_{11} \wedge s_{1(n+2)}=s_{2} \wedge s'_2 = s_{31} \wedge s_{3(m+1)}=s'\\
-\displaystyle{
-\set{\gamma''}=\mybigdotcup_{i=1}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup}\\
-{}~\qquad~\displaystyle{ \mybigdotcup_{i=1}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{1}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
+where we obtain the conclusion of the lemma, as required with the following assertions (derived from previous assertions):
+\begin{gather*}
+s_{10}=s_{10} \wedge s_{1(n+2)}=s_{2} \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
+\begin{align*}
+\alpha''=&\alpha\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}\subst{\Post_{10}} = \alpha\subst{\bigotimes_{j=n+1}^{0}\Post_{1j}}\\
+\set{\gamma''}=&\mybigdotcup_{i=0}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup\\
+&\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }
 \\
-\Pred=\bigwedge_{i=1}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{1}\Post_{1j}}\land\\ 
-{}~\qquad\quad\Big(\bigwedge_{i=1}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{1}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}}\Big)\\
-\Post=\bigotimes_{j=m}^{1}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}
-$
+\Pred=&\bigwedge_{i=0}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{0}\Post_{1j}}\land\\ 
+&\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{0}\Post_{1j}}\Big)
+\\
+\Post=&\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{0}\Post_{1j}
+\end{align*}
+\end{gather*}
 
@@
 
-These two cases above prove the implication with $n=0$ and $m=0$.
+These two cases above prove the implication with $n=-1$ and $m=-1$.
 
@@
 
-\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau open transitions such $n_1=n+m+1$, hence by simplification we have (strictly speaking, by induction we might also have the case $\alpha=\tau\land\set \gamma=\emptyset\land \ldots$ but in this case, rule \WTUn~ allows us to obtain a similar reduction with $n_1=1$):
+\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau open transitions such $n_1=n+m+3$, hence by simplification we have (strictly speaking, by induction we might also have the case $\alpha=\tau\land\set \gamma=\emptyset\land \ldots$ but in this case, rule \WTUn~ allows us to obtain a similar reduction with $n_1=1$):
 \begin{mathpar}
@@
 
-\item Similarly, a series of $m_1$ open transitions such that $m_1=n+m+1$   can be simplified as follows: 
+\item Similarly, a series of $m_1$ open transitions such that $m_1=n+m+3$   can be simplified as follows: 
 \begin{mathpar}
@@
 
-\item Concerning the middle reduction, by induction hypothesis there exist a set of open transitions in $\mathcal{T}$ such that:
+\item Concerning the middle reduction, by induction hypothesis there exists a set of open transitions in $\mathcal{T}$ such that:
 \begin{mathpar}
@@
 \end{mathpar}
-where\\
-$
-\alpha''=\alpha'\displaystyle{\subst{\bigotimes_{j=n_2}^{0}\Post_{2j}}}\\
+where
+\begin{gather*}
 s'=s_{20} \wedge s_{2(n_2+1)}=s_2 \wedge  s_2' = s_{20}' \wedge s_{2(m_2+1)}'=s''\\
-\displaystyle{
-\set{\gamma_2}=\mybigdotcup_{i=0}^{n_2} \vis{\set{\beta_{2i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{2 j} } }  \dotcup  \vis{\set{\beta'}\subst{\bigotimes_{j=n_2}^{0}\Post_{2j}}} \dotcup}\\~\qquad
- \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{2i}} \subst{\bigotimes_{j=i-1}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j=n_2}^{0}\Post_{2j}} }
+\begin{align*}
+\alpha''=&\alpha'\subst{\bigotimes_{j=n_2}^{0}\Post_{2j}}\\
+\set{\gamma_2}=&\mybigdotcup_{i=0}^{n_2} \vis{\set{\beta_{2i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{2 j} } }  \dotcup  \vis{\set{\beta'}\subst{\bigotimes_{j=n_2}^{0}\Post_{2j}}} \dotcup\\
+&
+ \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{2i}} \subst{\bigotimes_{j=i-1}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j=n_2}^{0}\Post_{2j}}}
 \\
-\Pred_2=\bigwedge_{i=0}^{n_2}\Pred_{2i}\subst{\bigotimes_{j=i-1}^{0}\Post_{2j}}\land\Pred\,' \subst{\bigotimes_{j={n_2}}^{0}\Post_{2j}}\land\\ 
-~\qquad\quad\Big(\bigwedge_{i=0}^{m_2}\Pred\,'_{2i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}}\Big)\\
+\Pred_2=&\bigwedge_{i=0}^{n_2}\Pred_{2i}\subst{\bigotimes_{j=i-1}^{0}\Post_{2j}}\land\Pred\,' \subst{\bigotimes_{j={n_2}}^{0}\Post_{2j}}\land\\ 
+&\Big(\bigwedge_{i=0}^{m_2}\Pred\,'_{2i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}}\Big)\\
 \Post_2=\bigotimes_{j=m_2}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}
-$
+\end{align*}
+\end{gather*}
 
@@
 such that\\
-
-$
-s_{4i}= \left\{
- \begin{array}{ll}
+\begin{align*}
+s_{4i}=\begin{cases}
 			s_{1i} & \mbox{if }i<n_1\\
-s_{2i-n_1} & \mbox{if }i\geq n_1\\
-\end{array}
-\right.  \qquad \qquad
-s_{5i}= \left\{
- \begin{array}{ll}
+			s_{2i-n_1} & \mbox{if }i\geq n_1
+	   \end{cases}
+&\qquad\qquad\qquad&
+s_{5i}=\begin{cases}
 			s_{3i} & \mbox{if }i<m_1\\
-s_{2i-m_1}' & \mbox{if }i\geq m_1\\
-\end{array}
-\right. \\
-$
-\\
+s_{2i-m_1}' & \mbox{if }i\geq m_1
+	\end{cases}\\
+\end{align*}
 
@@
 s\!=\!s_{40} \wedge s_{4(n_1+n_2+1)}\!=s_2 \wedge s_2' = s_{50} \wedge s_{5(m_1+m_2+1)}\!=\!s'\\
-~~\\
-\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2} \vis{\set{\beta_{4i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{4 j} } }  \dotcup  \vis{\set{\beta'}\subst{\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}}\dotcup }\\~\!\qquad\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta_{5i}}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{5i}\shortotimes\Post\,'\shortotimes\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4i}} }
+\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2} \vis{\set{\beta_{4i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{4 j} } }  \dotcup  \vis{\set{\beta'}\subst{\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}}\dotcup }\\
+{}~\!\qquad\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta_{5i}}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{5i}\shortotimes\Post\,'\shortotimes\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4i}} }
 \\
@@
 \bigwedge_{i=0}^{n_1+n_2}\!\!\Pred_{4i}\subst{\bigotimes_{j=i-1}^{0}\Post_{4j}}\land\Pred\,' \subst{\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\!\Post_{4j}}\land}\\ 
-~\qquad\quad\bigwedge_{i=0}^{m_1+m_2}\Pred_{5i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{5j}\shortotimes\Post\,'\shortotimes\!\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\!\Post_{4j}}\\
+{}~\qquad\quad\bigwedge_{i=0}^{m_1+m_2}\Pred_{5i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{5j}\shortotimes\Post\,'\shortotimes\!\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\!\Post_{4j}}\\
 \Post=\bigotimes_{j=m_1+m_2}^{0}\!\!\!\Post_{5j}\shortotimes\Post\,'\shortotimes\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\Post_{4j}
@@
 
- Let $A_1 = <J,\mathcal{S}_1, s_0,
-    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata.
-Let $<J,\mathcal{S}_1, s_0,
-    \WT_1>$ and $<J,\mathcal{S}_2,t_0,  \WT_2>$ be the
+ Let $A_1 = <\!J,\mathcal{S}_1, s_0,
+    \mathcal{T}_1\!>$ and $A_2 = <\!J,\mathcal{S}_2,t_0,  \mathcal{T}_2\!>$ be open automata; $<\!J,\mathcal{S}_1, s_0,
+    \WT_1\!>$ and $<\!J,\mathcal{S}_2,t_0,  \WT_2\!>$ be the
 weak open automata derived from $A_1$ and $A_2$ respectively.
@@
  and  \\
-$\Pred_{s,t} \land \Pred_{OT}\implies\\
+$\Pred_{s,t} \land \Pred_{OT}\!\implies\!
 \displaystyle{\bigvee_{x\in X}
@@
      \land \alpha\!=\!\alpha_x \!\land\!  
-     \Pred_{s',x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}$
+     \Pred_{s',x}\subst{\Post_{OT}\!\uplus\!\Post_{OT_x}}\right)}$
 
@@
 
-\begin{proof} Note that Definition \ref{def-Weak-bisim} is a particular case of the definition above, thus we only need to prove one direction of the equivalence between the two definition, namely: \\
+\begin{proof} Note that Definition \ref{def-Weak-bisim} is a particular case of the definition above, thus we only need to prove one direction of the equivalence between the two definitions, namely: \\
 ($\Rightarrow$) We prove that Definition \ref{def-Weak-bisim} implies the definition above. In other words,
@@
          {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T}_1  \wedge
-
+\\{\qquad\qquad\qquad\qquad\qquad}
 \openrule
@@
 \gamma_j^{j\in J'}=\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup}\\
-~\qquad\qquad\!\displaystyle{\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
+{}~\qquad\qquad\!\displaystyle{\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
 \\
 \Pred_{OT}=\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=n}^{0}\Post_{1j}}\land\\ 
-~\qquad\qquad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}}\Big)\\
+{}~\qquad\qquad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}}\Big)\\
 \Post_{OT}=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}$
 
-For the sake of simplicity, we prove the rule in the  restricted case where $n$ and $m$ are equal to $1$, hence a single tau open transition will be considered on each side of the potentially visible one.
+For the sake of simplicity, we prove the rule in the  restricted case where $n$ and $m$ are equal to $0$, hence a single tau open transition will be considered on each side of the potentially visible one.
 The proof may be easily generalized to the multiple tau open transitions by using the same reasoning and \WTTrois~ rule.
@@
 It remains to be proven that the following statement holds:\\
-$\Pred_{s,t} \land \Pred\implies\\
+$\Pred_{s,t} \land \Pred\implies
  \displaystyle{\bigvee_{x\in X}} 
@@
 Moreover, we have the following  statement:\\
-$\Pred_{s,t} \land \Pred_1\implies\\
+$\Pred_{s,t} \land \Pred_1\implies
  \displaystyle{\bigvee_{a\in A}}
@@
   \!\! ( \forall j\in J_a. \vis{\beta_{1j}}\!=\!\gamma_{ja}\!  \land\! \Pred_{OT_a}\! \land\!
-     \Pred_{s_{11},a}\subst{\Post_1\uplus\Post_{OT_a}}) \wedge \Pred_2\subst{\Post_1\uplus\Post_{OT_a}}  \\
+     \Pred_{s_{11},a}\subst{\Post_1\uplus\Post_{OT_a}}) \wedge \Pred_2\subst{\Post_1\uplus\Post_{OT_a}}  
 $
@@
      \!\land(\Pred_{s_{11},a}\wedge\Pred_2)\subst{\Post_1\uplus\Post_{OT_a}} \right)$\\
-By replacing the inner predicate $(\Pred_{s_{11},u_a}\wedge\Pred_2)$ by the conclusion of the  statement given in case 2,  the formula becomes: \\
-$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies\\
-\displaystyle{\bigvee_{a\in A}}
+By replacing the inner predicate $(\Pred_{s_{11},u_a}\wedge\Pred_2)$ by the conclusion of the  statement given in case 2,  the formula becomes: 
+\begin{multline*}(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies\\
+{\bigvee_{a\in A}}
    \!\!(\forall j\in J_a. \vis{\beta_{1j}}\!\!=\!\gamma_{ja}  \land \Pred_{OT_a}
-      \land (\displaystyle{\bigvee_{b\in B}}(
+      \land ({\bigvee_{b\in B}}(
     \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}  \land \Pred_{OT_{b}}\!\land 
-    \alpha'\!=\!\alpha_{2 b} \land\\ \Pred_{s_{21},b}\subst{\Post_2\uplus\Post_{OT_{b}}})\subst{\Post_1\uplus\Post_{OT_a}})$\\
-This can be rewritten into:\\
-$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1} \implies\\
-\displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}} 
+    \alpha'\!=\!\alpha_{2 b} \land\\ \Pred_{s_{21},b}\subst{\Post_2\uplus\Post_{OT_{b}}})\subst{\Post_1\uplus\Post_{OT_a}})
+\end{multline*}
+
+This can be rewritten into:
+\begin{multline*}(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1} \implies\\
+{\bigvee_{a\in A}}\, {\bigvee_{b\in B}} 
 (\forall j\in J_a.
 \vis{\beta_{1j}}\!\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-\vis{\beta_{2j}}\!=\!\gamma_{jb}\subst{\Post_1\uplus\Post_{OT_a}}   \land\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_1\uplus\Post_{OT_a}} \land  (\alpha'\!=\!\alpha_{2 b}) \subst{\Post_1\uplus\Post_{OT_a}} \land\\ \Pred_{s_{21},b}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
+\vis{\beta_{2j}}\!=\!\gamma_{jb}\subst{\Post_1\uplus\Post_{OT_a}}   \land\Pred_{OT_a} \land \\ \Pred_{OT_{b}} \subst{\Post_1\uplus\Post_{OT_a}} \land  (\alpha'\!=\!\alpha_{2 b}) \subst{\Post_1\uplus\Post_{OT_a}} \land \\ \Pred_{s_{21},b}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})
+\end{multline*}
 Since $Post_1$  does not act on $\gamma_{jb}$, nor on $ \Pred_{OT_{b}}$ and $  \alpha_{2}$.
-As well $\Post_{OT_a}$  does not act on $\alpha'$, nor on  $\beta_{2j}$ the formula can be simplified as follows:\\
-$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies\\
+As well $\Post_{OT_a}$  does not act on $\alpha'$, nor on  $\beta_{2j}$ the formula can be simplified as follows:
+\begin{multline*}(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies\\
 \displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}} 
@@
 \vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-\vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jb} \subst{\Post_{OT_a}}  \land\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_{OT_a}} \land \alpha'\subst{\Post_1}=\alpha_{2 b} \subst{\Post_{OT_a}} \land\\ \Pred_{s_{21},b}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\
-Finally, the conjunction with the term $\Pred_3\subst{\Post_2\shortotimes\Post_1}$ of the both sides of the implication and rewriting, we get:\\
-$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\implies \\
+\vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jb} \subst{\Post_{OT_a}}  \land\Pred_{OT_a} \land \\ \Pred_{OT_{b}} \subst{\Post_{OT_a}} \land \alpha'\subst{\Post_1}=\alpha_{2 b} \subst{\Post_{OT_a}} \land\\ \Pred_{s_{21},b}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})\end{multline*}
+Finally, the conjunction with the term $\Pred_3\subst{\Post_2\shortotimes\Post_1}$ of the both sides of the implication and rewriting, we get:
+\begin{multline*}(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\implies \\
 \displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}} 
 (\forall j\in J_a.\vis{\beta^1_j}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-\vis{\beta_{2j}}\subst{\Post_1}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}\land \Pred_{OT_a}\land\Pred_{OT_{b}}\subst{\Post_{OT_a}} \land  \alpha'\subst{\Post_1}= \alpha_{2 b} \subst{\Post_{OT_a}} \land (\Pred_{s_{21},v_b} \land  \Pred_3)\\ \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{b}}\shortotimes\Post_{OT_a}})$\\
+\vis{\beta_{2j}}\subst{\Post_1}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}\land \Pred_{OT_a}\land\\\Pred_{OT_{b}}\subst{\Post_{OT_a}} \land  \alpha'\subst{\Post_1}= \alpha_{2 b} \subst{\Post_{OT_a}} \land (\Pred_{s_{21},v_b} \land  \Pred_3)\\ \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{b}}\shortotimes\Post_{OT_a}})\end{multline*}
 Again note that because of the domain  of the substitution is independent from some predicates and expressions, we removed $\Post_1$ and  we  added the term $\Post_{OT_{b}}\shortotimes\,\Post_{OT_a}$ in the substitution of the right side of the implication.\\
 Finally, by replacing the predicate $(\Pred_{s_{21},b} \land  \Pred_3)$
-by the conclusion of the  implication given in case 3, we get:\\
-$\Pred_{s,t} \land \underbrace{\Pred_1\land \Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}}_{\Pred_{OT}}\implies\\
- \displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}}\, \displaystyle{\bigvee_{c\in C}} 
+by the conclusion of the  implication given in case 3, we get:
+\begin{multline*}\Pred_{s,t} \land \underbrace{\Pred_1\land \Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}}_{\Pred_{OT}}\implies\\
+ {\bigvee_{a\in A}}\, {\bigvee_{b\in B}}\, {\bigvee_{c\in C}} 
 (\forall\! j\in\! J_a.\vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \!\in\! J_{b}.\vis{\beta_{2j}\subst{\Post_{OT_a}}}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}  \land \\
@@
    \underbrace{\Pred_{OT_a}\land\Pred_{OT_{b}} \subst{\Post_{OT_a}} \land 
-  \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}}_{\Pred} \land  \underbrace{\alpha'\subst{\Post_1}}_{\alpha}=\underbrace{\alpha_{2 b} \subst{\Post_{OT_a}}}_{\alpha''} \land\\ \Pred_{s_{31},c}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{c}}\shortotimes \Post_{OT_{b}}\shortotimes\Post_{OT_a}}_{\Post}})$\\
-The three for all statements (on $J_a$, $J_b$, and $J_c$) can be concatenated using $\dotcup$, the list union lifted to indexed sets (if $\gamma=\gamma'$ and $\gamma''=\gamma'''$ then $\gamma\dotcup\gamma''=\gamma'\dotcup\gamma'''$).\\
-$\forall j\in J_a\uplus J_b\uplus J_c.
+  \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}}_{\Pred} \land  \underbrace{\alpha'\subst{\Post_1}}_{\alpha}=\underbrace{\alpha_{2 b} \subst{\Post_{OT_a}}}_{\alpha''} \land\\ \Pred_{s_{31},c}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{c}}\shortotimes \Post_{OT_{b}}\shortotimes\Post_{OT_a}}_{\Post}})
+\end{multline*}
+The three for all statements (on $J_a$, $J_b$, and $J_c$) can be concatenated using $\dotcup$, the list union lifted to indexed sets (if $\gamma=\gamma'$ and $\gamma''=\gamma'''$ then $\gamma\dotcup\gamma''=\gamma'\dotcup\gamma'''$).
+\begin{multline*}\forall j\in J_a\uplus J_b\uplus J_c.
 \vis{\beta_{1j}}\dotcup \vis{\beta_{2j}\subst{\Post_{OT_a}}}\dotcup \vis{\beta_{3j} \subst{\Post_2\shortotimes\Post_1}}=\\ ~\hspace{5.5cm} \gamma_{j a} \dotcup \gamma_{jb} \subst{\Post_{OT_a}}  \dotcup \gamma_{jc} \subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}
-$ \\
+\end{multline*}
 We have  $s_{31}=s'$, so can rewrite the formula:\\
-$\Pred_{s,t} \land \Pred_{OT}\implies\\
+$\Pred_{s,t} \land \Pred_{OT}\implies
 \displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}}\, \displaystyle{\bigvee_{c\in C}} 
@@
 This re-indexing allows us to conclude:\\
-$\Pred_{s,t} \land \Pred_{OT}\implies\\\
+$\Pred_{s,t} \land \Pred_{OT}\implies
  \displaystyle{\bigvee_{x\in X}} 
@@
 \]
-with \\
-
+with 
 $\set{\gamma'_{3p}}=\set{\beta_{3p}}, \Pred\,'_{3p} =\Pred_{3p}, \Post\,'_{3p} =\Post_{3p}$

### 2020-02-26 2016-Weak-FH-Bisim/WeakBisim.tex
proofs again

@@
 \subsection{Composition properties}\label{sec:app-composition}
-This section gives detailed lemmas and their proofs, these are the equivalent of the composition lemmas for open transitions, but applied to weak automata that give the semantics of open pNets.
-
+This section gives decomposition/composition lemmas and their proofs, these are the equivalent of the composition lemmas for open transitions, but applied to weak open automata.
 \begin{lemma}[Weak open transition decomposition]\label{lem-decomposeWOT} 
@@
 where\\
+ for all $l\in L$: $s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
 $\alpha=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}}$\\
- for all $l\in L$: $s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
 $\displaystyle{
-\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!
-\Post_{1j}}}\dotcup\  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}}} \dotcup \\ ~\quad\,\qquad \displaystyle{\mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }}
+\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\! \Post_{1j}}}\dotcup\  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}}} \dotcup \\ 
+{}~\quad\,\qquad \displaystyle{\mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }}
 \\
 \Pred=\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\land\\ 
-~\qquad\quad\bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
+{}~\qquad\quad\bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
 \Post=\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}$\\
@@
 \end{mathpar}
-where:\\
-$\alpha''=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}}$\\
+where
+$\alpha''=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}}$\\
 On the other hand, we have:
-$\alpha=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}}\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}}}=\alpha''\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}}}$.\\
-As $\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}}}$ has no effect on variables of $P$ and thus on variables of $\alpha$, so we have $\alpha=\alpha''$.
+$\alpha=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}}\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,''_{1j}}}=\alpha''\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,''_{1j}}}$.\\
+As $\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,''_{1j}}}$ has no effect on variables of $P$ and thus on variables of $\alpha$, so we have $\alpha=\alpha''$.
 \\
@@
 ${(\gamma_j')}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}}} \dotcup\\
-~~\qquad \qquad\qquad\qquad\qquad \mybigdotcup_{i=0}^{m_2}
+{}~~\qquad \qquad\qquad\qquad\qquad \mybigdotcup_{i=0}^{m_2}
 \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}} }\\
 \Pred\,'=\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}\land\\ 
-~\qquad\qquad\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}\\
+{}~\qquad\qquad\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}\\
 \Post'=\bigotimes_{j=m_2}^{0}\!\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}$
 
-Note that for all $j\in J\setminus \Holes(Q)$, $\gamma_j' = \gamma_j$ because for all $l$ $\Post'_{1l}$ coincide with $\Post_{1l}$ on the variables of $\beta_{1ij}$, and similarly for $\Post'_2$ and $\Post'_{3l}$.
+Note that for all $j\in J\setminus \Holes(Q)$, $\gamma_j' = \gamma_j$ because for all $l$ $\Post\,'_{1l}$ coincide with $\Post_{1l}$ on the variables of $\beta_{1ij}$, and similarly for $\Post\,'_2$ and $\Post\,'_{3l}$.
 %Concerning $\gamma'_{j_0}$ we have:
@@
 
-We denote the following predicate (we will need it for reasoning on the global predicate and will reason on it along the proof):\\
+We introduce the following predicate (we will need it for reasoning on the global predicate and will reason on it along the proof):\\
 $\begin{array}{l}\displaystyle{

### 2020-02-26 2016-Weak-FH-Bisim/WeakBisim.tex
proofs again checked all but a bit fast on the last thms

@@
 $\\ 
-In this equation, and using case 1 above for all $k\in [0\ldots n_1]$ there is a $p\in [0..m_1]$ such that $\alpha_{1p}=\alpha_k$ (following the re-indexing done in the removal of steps where $Q$ does not move), we have $\Pred_{1p}$ contains $ \alpha_{1p}=\beta_{1 p j_0}$.
-Because $\beta_{1 p j_0}$ only contains variables of $P$ and $\alpha_k$ only variables of $Q$:
+In this equation, and using case 1 above for all $k\in [0\ldots n_1]$ there is a $p\in [0..m_1]$ such that $\alpha_{1p}=\alpha_k$ (following the re-indexing done in the removal of steps where $Q$ does not move), we know that $\Pred_{1p}$ contains the predicate $( \alpha_{1p}=\beta_{1 p j_0})$.
+Because $\beta_{1 p j_0}$ only contains variables of $P$ and $\alpha_k$ only variables of $Q$, we have:
 \begin{equation*}
@@
 We can obtain similar equations for $\alpha_{n_1+1}$ related with $\beta_{2 j_0}$ and the  $\alpha_k$ for $k\geq n_1+2$ related with $\beta_{3 p j_0}$ for some $p$.
-Note that the substitutions are however more complex.
+Note that the substitutions are however more complex in the other cases.
 Overall we obtain (we skip here the details about the three cases 1, 2, and 3 above that all fall into the same equation because of the re-indexing we perform): 
@@
 Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (they are $\tau$ transitions).
-By considering the sequence of $\tau$ and non-$\tau$ actions we split the sequence of actions into $n+1$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many $\tau$ ones.
+By considering the sequence of $\tau$ and non-$\tau$ actions we split the sequence of actions into $n+1$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many non-observable ($\tau$) ones.
 
@@
 \end{mathpar}
+With:
+$\forall l \in L_Q. v_{kl}=v_{(n'_{k})l} \wedge v_{kl}'=v_{(n'_k)l}$\\
 $\alpha_k'=\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}}$\\
-$\forall l \in L_Q. v_{kl}=v_{(n'_{k})l} \wedge v_{kl}'=v_{(n'_k)l}$\\
 $\displaystyle{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=\displaystyle{\mybigdotcup_{i=n'_{k}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}} \dotcup\\
-~~\qquad \qquad\qquad\mybigdotcup_{i=n_k+1}^{n'_{k+1}-1}
+{}~~\qquad \qquad\qquad\mybigdotcup_{i=n_k+1}^{n'_{k+1}-1}
 \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}} \subst{\bigotimes_{l=i-1}^{n_k\!+\!1}\!\Post\,''_{l}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}} }\\
@@
 \Pred_k=\bigwedge_{i=n'_{k}}^{n_k\!-\!1}\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\Pred\,''_{n_k} \subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\\ 
-~\qquad\quad\bigwedge_{i=n_k+1}^{n'_{k+1}-1}\!\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\!\Post\,''_{j}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{j}}
+{}~\qquad\quad\bigwedge_{i=n_k+1}^{n'_{k+1}-1}\!\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\!\Post\,''_{j}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{j}}
 \\
@@
 
-We need now to show that this set of WOT verify the conditions of the lemma, i.e. it is a set of WOT of the form:
+We need now to show that this set of WOT verifies the conditions of the lemma, i.e. it is a set of WOT of the form:
 \[	Q\models{\openrule
@@
 \begin{split}
-\gamma_j^{j\in J}&=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!
-\Post_{1j}}}\dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }\\
+\gamma_j^{j\in J}=&\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!
+\Post_{1j}}}\dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup\\& \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }\\
 \end{split}\end{equation*}
@@
 Overall, we have
+
+$\forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i$ (see above)\\
 {\scriptsize \begin{equation*}
@@
 }
-$\forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i$ (see above)\\
 $\Pred = \displaystyle{\Pred\,'
@@
 which is exactly what is needed.\\
-Finally we have:\\
+Finally we have~~
 $\Post=\displaystyle{\Post\,' \uplus \bigotimes_{p=n}^0
-		\Post_p}$\\
-Because
+		\Post_p}$\quad
+because
 \begin{equation*}
@@
 \begin{lemma}[Weak open transition composition]\label{lem-Weakcompose1} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
-	Suppose $j_0\in J$  and additionally:\\[-2ex]
+	Suppose $j_0\in J$  and:\\[-1ex]
 \begin{mathpar}
@@
 \end{mathpar}
-Let 
+Let\\[-3ex] 
 \begin{mathpar}
@@
 \end{mathpar}
-Then, we have\\[-2ex]
+Then, we have\\[-3ex]
 	\[ P[Q]_{j_0}  
@@
 \end{mathpar}
-such that\\ 
-$\alpha_Q=\alpha'_Q\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$\\
-$s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\
+such that
+
 \begin{small}
-$\displaystyle{
-\set{\gamma}=\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{j=h-1}^{0}\!\! \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=k}^{0}\Post_{1j}}} \dotcup}$\\
- $~~\hspace{1.8em}\displaystyle{ \mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{j=h-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=k}^{0}\Post_{1j}} }}
-\\
-\Pred_Q=\bigwedge_{h=0}^{k}\!\big(\Pred_{1h}\subst{\bigotimes_{j=h-1}^{0}\Post_j^1}\big)\land \Pred_2\subst{\bigotimes_{h=k}^{0}\Post_{1h}}\land\\~\qquad\qquad \bigwedge_{h=0}^{k'}\!\Pred_{3h}\subst{\bigotimes_{j=h-1}^{0}{\Post_{3j}}\otimes{\Post_2}  \otimes\bigotimes_{h=k}^{0}\Post_{1h}}
-\\
-\Post_Q=\bigotimes_{h=k'}^{0}\Post_{3h}\otimes\Post_2\otimes\bigotimes_{j=k}^{0}\Post_{1j}
-$
+$s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$
+\begin{align*}
+\alpha_Q=&\alpha'_Q\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}\\
+\set{\gamma}=&\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{j=h-1}^{0}\!\! \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=k}^{0}\Post_{1j}}} \dotcup%\\
+		%&
+ \mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{j=h-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=k}^{0}\Post_{1j}} }\\
+\Pred_Q=&\bigwedge_{h=0}^{k}\!\big(\Pred_{1h}\subst{\bigotimes_{j=h-1}^{0}\Post_j^1}\big)\land \Pred_2\subst{\bigotimes_{h=k}^{0}\Post_{1h}}\land\\
+&		\bigwedge_{h=0}^{k'}\!\Pred_{3h}\subst{\bigotimes_{j=h-1}^{0}{\Post_{3j}}\otimes{\Post_2}  \otimes\bigotimes_{h=k}^{0}\Post_{1h}}\\
+\Post_Q=&\bigotimes_{h=k'}^{0}\Post_{3h}\otimes\Post_2\otimes\bigotimes_{j=k}^{0}\Post_{1j}
+\end{align*}
+
 \end{small}
@@
 %		{\Post_p}\!\!'$\\ 
-\item We proceed in the same way as the first item for $k'$ last weak open transitions, and we obtain $k'$ open tau transitions.\\
+\item We proceed in the same way as the first item for $k'$ last weak open transitions, and we obtain $k'$ open tau transitions.
 \end{enumerate}
@@
 	\ostate{{{s'}^{i\in L}_{i}\uplus s_{3(k'+1)}}}}\] 
-where\\
+where ~~
 $\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$
@@
 \Post_{1i} } }  \dotcup  \vis{({\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2})\subst{\bigotimes_{i=k}^{0}\Post_{1i}}} \dotcup}$ \\
-$~~\hspace{1.8em}\displaystyle{\mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{i=h-1}^{0}\!\!\Post_{3i}\shortotimes\Post_2\shortotimes\bigotimes_{i=k}^{0}\Post_{1i}} }}$\\
-$~~\hspace{0.6em}=\set{\gamma}\uplus\vis{\beta_j^{\in J\setminus \{j_0\}}} \quad$  because $\Post_{1j}$  does not act on variables of $\beta_j$.  \\
+${}~~\hspace{1.8em}\displaystyle{\mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{i=h-1}^{0}\!\!\Post_{3i}\shortotimes\Post_2\shortotimes\bigotimes_{i=k}^{0}\Post_{1i}} }}$\\
+${}~~\hspace{0.6em}=\set{\gamma}\uplus\vis{\beta_j^{\in J\setminus \{j_0\}}} \quad$  because $\Post_{1j}$  does not act on variables of $\beta_j$.  \\
 \begin{small}
@@
 $\\
-$\Post_c=\displaystyle{(\bigotimes_{i=k'}^{0}{\Post_{3i}})\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}$\\
+$\Post_c=\displaystyle{(\bigotimes_{i=k'}^{0}{\Post_{3i}})\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}$
 \end{small}
-\noindent Note that we have $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\
+
+\noindent Note that we have $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$
 
@@
 (\alpha'_Q=\beta_{j_0})\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\\
-&=\Pred_Q\land\Pred\land \alpha_Q=\beta_{j_0}\\
-&\\
-\Post_c&=\Post\uplus\Post_Q
+&=\Pred_Q\land\Pred\land \alpha_Q=\beta_{j_0}\\[.3ex]
+\Post_c&=\Post\uplus\Post_Q \\[-3ex]
 \end{split}
 \end{equation*}
-%\qed
 \end{proof}
@@
 \end{mathpar}
+
 Let 
@@
 $\gamma_j^{j\in J}=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \dotcup \, \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}}\, \dotcup\\
-~\qquad\quad \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{3p}} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}$\\
+{}~\qquad\quad \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{3p}} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}$\\
 %\end{multline*}
@@
 $\Pred=\displaystyle{\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\big)\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land}$\\ 
-$~~\qquad\quad\displaystyle{\bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}}$\\
+${}~~\qquad\quad\displaystyle{\bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}}$\\
 $\Post=\displaystyle{\bigotimes_{p=m_2}^{0}\Post_{3p}\otimes\Post_2\otimes\bigotimes_{j=m_1}^{0}\Post_{1j}}$\\
@@
 Where\\
-$
+{\small $
 \alpha''=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}\\
@@
  \mybigdotcup_{i=0}^{m_1}\set{\gamma'_{1i}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{1k}}\,\dotcup\,
-\set{\gamma'_{2}}\subst{\bigotimes_{k=m_1}^{0}\Post\,'_{1k}}\,\dotcup}\\
-\displaystyle{~\qquad \mybigdotcup_{i=0}^{m_2}\set{\gamma'_{3i}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}
+\set{\gamma'_{2}}\subst{\bigotimes_{k=m_1}^{0}\Post\,'_{1k}}\,\dotcup
+ \mybigdotcup_{i=0}^{m_2}\set{\gamma'_{3i}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}
 }
 \\
-%\mybigdotcup_{i=0}^{m_1} (\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{1pj}^{j\in J_{3p}\setminus \{j_0\}}})\subst{\bigotimes_{j=i-1}^{0} \Post_{1j}' }  
-%\dotcup  (\gamma_{m j}^{j\in J_m}\uplus\vis{\beta_{2j}^{j\in J_2\setminus \{j_0\}}})\subst{\bigotimes_{j={m_1}}^{0}\Post_{1j}'}}\\
-%\displaystyle{\qquad  \dotcup \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
-%\\
 \Pred\,''=\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\ 
-~\qquad\qquad\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_2}^{0}\Post\,'_{1j}}\\
+{}~\qquad\qquad\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_2}^{0}\Post\,'_{1j}}\\
 \Post\,''=\bigotimes_{j=m_2}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}
 $
+}
 
@@
 &=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\
-&\qquad \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\Big)\\&\qquad
+&\qquad \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\Big)%\\&\qquad
 \land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i\\&\qquad
@@
 ~\quad\bigwedge_{i=m+1}^{n}(\beta_{3{n'_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j=n'_i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\Big)\\
-&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\big)\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\&\qquad \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\Big)\\&\qquad
+&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\big)\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\&\qquad \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\Big)%\\&\qquad
 \land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i\\&\qquad
@@
 		\Post_P\uplus \Post_Q}
-	{\ostate{S_P\uplus S_Q} \OTWeakarrow {\alpha}
+	{\ostate{S_P\uplus S_Q} \OTarrow {\alpha}
 		\ostate{S'_P\uplus S'_Q}
@@
 		\Post_Q}
-	{\ostate{S_P} \OTWeakarrow {\alpha}
+	{\ostate{S_P} \OTarrow {\alpha}
 		\ostate{S'_P}}
@@
 		\Post_Q}
-	{\ostate{S_Q} \OTWeakarrow {\alpha_Q}
+	{\ostate{S_Q} \OTarrow {\alpha_Q}
 		\ostate{S'_Q}}
@@
 	{
-		\vis{\beta_j^{j\in( J_P}}\uplus\gamma_{j x}^{j\in J_Q}, 
+		\vis{\beta_j^{j\in J_P}}\uplus\gamma_{j x}^{j\in J_Q}, 
 		\Pred_P\land \Pred_{Q' x},  
@@
 Side conditions necessary to prove weak-FH bisimulations are:
-
 \[\forall x.\, (S'_P\uplus S'_Q,S'_P\uplus S'_{Q' x}| \Pred_{Q,Q' x})\in\mathcal{R}\]
@@
 (\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x}\land \forall j\in J_P.\, \vis{\beta_j}=\vis{\beta_j}))\Rightarrow\\
-& (\Pred_P\land \Pred_{Q' x}\land\\ &~~\alpha=\alpha \land \Pred_{Q,Q' x}\subst{\Post_P\uplus\Post_{Q' x}\uplus \Post_{Q}}) \Big)
+& (\Pred_P\land \Pred_{Q' x}\land\\ &\quad\alpha=\alpha \land \Pred_{Q,Q' x}\subst{\Post_P\uplus\Post_{Q' x}\uplus \Post_{Q}}) \Big)
 \end{split}
@@
  \begin{proof}   Consider $P$ weak FH-bisimilar to $P'$.
-It means, there exist a FH-bisimulation $\mathcal{R}_{P,P'}$ relating the two pNets $P$ and $P'$.
+There exist a FH-bisimulation $\mathcal{R}_{P,P'}$ relating $P$ and $P'$.
 We define a relation $\mathcal{R}$ relating states of $P[Q]_{j_0}$ with states of $P'[Q]_{j_0}$:
@@
 	{
-		\vis{\beta_j^{j\in( J_Q}}\uplus\gamma_{j x}^{j\in J_Q}, 
+		\vis{\beta_j^{j\in J_Q}}\uplus\gamma_{j x}^{j\in J_Q}, 
 		\Pred_{P' x}\land \Pred_Q,  
@@
 Side conditions necessary to prove weak-FH bisimulations are:
-
 \[\forall x.\, (S'_P\uplus S'_Q,S'_{P' x}\uplus S'_Q, \Pred_{P,P' x})\in\mathcal{R}\]
@@
 (\forall j\in J_P.\, \vis{\beta_j}\gamma_{j x} \land \forall j\in J_Q.\, \vis{\beta_j}=\vis{\beta_j} )\Rightarrow\\
-& (\Pred_{P' x}\land \Pred_Q\land\\ &~~\alpha_x=\alpha \land \Pred_{P,P' x}\subst{\Post_{P' x}\uplus\Post_P\uplus \Post_{Q}}) \Big)
+& (\Pred_{P' x}\land \Pred_Q\land\\ &\quad\alpha_x=\alpha \land \Pred_{P,P' x}\subst{\Post_{P' x}\uplus\Post_P\uplus \Post_{Q}}) \Big)
 \end{split}

### 2020-02-27 2016-Weak-FH-Bisim/WeakBisim.tex
Recupere example page 25 qui avait disparu

@@
 \subsection{Running example}
-- In section \ref{def:weakOT} we have shown the full satured weak automaton for both the specification and the implementation of the simple protocol.
-
-\TODO{Je ne pense pas que nous ayons un algo de bisim weak operationnel pour la publi, mais ca n'est pas completement impossible nonp[l;us...
-Au pire, argumenter intuitivement sur papier, en donnat les classes d'equivalence et les predicats.}
-
+In section \ref{def:weakOT} we have shown the full satured weak automaton for both the specification and the implementation of the simple protocol.
+We will show here how we can check if some given relation between these two automata is a weak FH-Bisimulation.
+
+\medskip
+\noindent
+Preliminary remarks:
   \begin{itemize}
-    \item[] Both pNets trivialy verify the ``non-observability''
+    \item Both pNets trivialy verify the ``non-observability''
       condition: the only vectors having $\tau$ as an action of a
       sub-net are of the form ``$< -, \tau, -> -> \tau$''.
+    \item We must take care of variable name conflicts: in our example, the state variables of the 2 systems already have different names, but the action parameters occuring in the transitions (m, msg, ec) are the same, that is not correct.
+In the tools, this is managed by the static semantic layer; in the following example, we have renamed all conflicting variables with 1 for the Spec, and 2 for the Impl.
+    \item In practice, we are dealing with finite representations of the (infinite) open automata.
+In \cite{PEPM}, we defined a slightly modified definition of the ``coverage'' proof obligation, in the case of strong FH-Bisimulation.
+This modification is required to manage in a finite way all possible instantiations of an OT.
+In the case of weak FH-Bisimulation, the proof obligation from definition \ref{def-Weak-bisim} becomes:
+
+ $\forall fv_{OT}. \{ \Pred \land \Pred_{OT}\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
+  \left[\exists fv_{OT_x}.\\
+    \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
+     \!\land\! \alpha\!=\!\alpha_x\! \land\!  
+     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)\right]}$
+
   \end{itemize}
 
-  Now consider the following triples:
+  Now consider relation $\mathcal{R}$ defined by the following triples:
+
+  \begin{tabular}{|c|c|l|}
+\hline
+    Spec state & Impl state & Predicate\\
+    \hline
+    b0 & $\ostate{000}$ & True\\
+    b0 & $\ostate{202}$ & True\\
+    b1 & $\ostate{100}$ & $\texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec}$\\
+    b1 & $\ostate{210}$ & $\texttt{b1\_msg = m1\_msg} \land \texttt{b1\_ec = m1\_ec}$\\
+    b1 & $\ostate{220}$ & $\texttt{b1\_msg = m2\_msg} \land \texttt{b1\_ec = m2\_ec}$\\
+    b1 & $\ostate{201}$ & $\texttt{b1\_msg = r1\_msg} \land \texttt{b1\_ec = r1\_ec}$\\
+    \hline
+    \end{tabular}
+
+  \medskip
+  Checking that $\mathcal{R}$ is a weak FH-Bisimulation means checking, for each of these triples, that each WOT of one the states corresponds to a set of WOTs of the other, using the conditions from Definition \ref{def-Weak-bisim}.
+  We give here two examples.
+
+  Consider the first triple from the table, and transition $WS_3(n)$ from state $\ostate{b0}$ for some fixed integer $n$. Its easy to guess that it will correspond to $WI_3(n)$ of $\ostate{000}$.
+
+  $ WS_3(n) = \openrule
+  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
+    (\texttt{b1\_msg}\gets \texttt{m}, \texttt{b1\_ec}\gets n)}
+  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
+  $
+
+$ WI_3(n) = \openrule
+  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
+    (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets n)}
+  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
+  $
+
+  Let check formally the conditions:
+
+\begin{itemize}
+  \item Their sets of active (non-silent) holes is the same: $\{P\}$.
+  \item Triple ($\ostate{b1},  \ostate{100},  \texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec}$) is in $\mathcal{R}$.
+  \item The verification condition \\
+    $\Pred \land \Pred_{OT}%\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
+   \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
+     \!\land\! \alpha\!=\!\alpha_x\! \land\!  
+     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}$
+
+\medskip Gives us:
+
+\TODO{Insert here $\forall \phi(m1,m2)$ }
+
+$True \land True\hspace{1cm} \implies\\ 
+\texttt{p-send(m1)} = \texttt{p-send(m2)}
+\land True
+\land \underline{\texttt{in(m1)}} = \underline{\texttt{in(m2)}}
+\land (\texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec})
+\subst{(\texttt{b1\_msg}\gets \texttt{m}, \texttt{b1\_ec}\gets n)
+  \uplus (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets n)}
+$
+
+\medskip That reduces to:
+
+$\forall \texttt{m1}. \exists \texttt{m2}.
+(\texttt{p-send(m1)} = \texttt{p-send(m2)}
+\land \texttt{in(m1)} = \texttt{in(m2)}
+\land \texttt{m}=\texttt{m} \land n=n)$
+
+\medskip That is a tautology.
+
+\end{itemize}
 
@@
 
-In Figure \ref{Appendix:SpecOA-partial} we show the weak oepn automaton of our implementation pNet. Details of the weak transitions is listed here:
+In Figure \ref{Appendix:SpecOA-partial} we show the weak open automaton of our implementation pNet. Details of the weak transitions is listed here:
 
@@
 
-\section{Examples of Lotos laws}
-Possible Lotos small examples:
-
-Strong bisim:\\
-1) Hiding:\\
-\centerline{hide \{g\} in a;B  ==  a; hide \{g\} in B  iff gatename(a)$\neq$g}\\
-\centerline{hide \{g\} in a;B  ==  i; hide \{g\} in B  iff gatename(a)$=$g}
-2) Disabling:\\
-\centerline{B1[>(B2[>B3) == (B1[>B2)[>b3}\\
-\centerline{(B1[>B2)[]B3 == B1[>B2}\\
-\centerline{B[>stop == B}\\
-\centerline{stop[>B == B}\\
-\centerline{exit(...)[>B == exit(...)[]B}\\
-3) Enabling:\\
-\centerline{B1>>(B2>>B3) == (B1>>B2)>>b3}\\
-\centerline{B>>stop == B|||stop}\\
-\centerline{stop>>B == stop}\\
-\centerline{exit>>B == i;B}\\
-4) Choice:\\
-\centerline{B1[](B2[]B3) == (B1[]B2)[]b3}\\
-\centerline{B1[]B2 == B2[]B1}\\
-\centerline{B[]stop == B}\\
-\centerline{B[]B == B}\\
-
-5) Others:\\
-\centerline{B1|[]|B2 == B1|||B2}\\
-
-Weak congruence:\\
-\centerline{a;i;B == a;B}\\
-\centerline{B[]i;B == i;B}\\
-and many others, often not easy to express without syntax for set operations,
-like e.g.:
-\centerline{}
-
-Weak equivalence:\\
-\centerline{i;B == B}
+%% \section{Examples of Lotos laws}
+%% Possible Lotos small examples:
+
+%% Strong bisim:\\
+%% 1) Hiding:\\
+%% \centerline{hide \{g\} in a;B  ==  a; hide \{g\} in B  iff gatename(a)$\neq$g}\\
+%% \centerline{hide \{g\} in a;B  ==  i; hide \{g\} in B  iff gatename(a)$=$g}
+%% 2) Disabling:\\
+%% \centerline{B1[>(B2[>B3) == (B1[>B2)[>b3}\\
+%% \centerline{(B1[>B2)[]B3 == B1[>B2}\\
+%% \centerline{B[>stop == B}\\
+%% \centerline{stop[>B == B}\\
+%% \centerline{exit(...)[>B == exit(...)[]B}\\
+%% 3) Enabling:\\
+%% \centerline{B1>>(B2>>B3) == (B1>>B2)>>b3}\\
+%% \centerline{B>>stop == B|||stop}\\
+%% \centerline{stop>>B == stop}\\
+%% \centerline{exit>>B == i;B}\\
+%% 4) Choice:\\
+%% \centerline{B1[](B2[]B3) == (B1[]B2)[]b3}\\
+%% \centerline{B1[]B2 == B2[]B1}\\
+%% \centerline{B[]stop == B}\\
+%% \centerline{B[]B == B}\\
+
+%% 5) Others:\\
+%% \centerline{B1|[]|B2 == B1|||B2}\\
+
+%% Weak congruence:\\
+%% \centerline{a;i;B == a;B}\\
+%% \centerline{B[]i;B == i;B}\\
+%% and many others, often not easy to express without syntax for set operations,
+%% like e.g.:
+%% \centerline{}
+
+%% Weak equivalence:\\
+%% \centerline{i;B == B}

### 2020-02-27 2016-Weak-FH-Bisim/WeakBisim.tex
fixed running ex page 25

@@
 Indeed only the visible actions of the holes must be compared and they form a list of actions, but of length at most one.
-Weak FH-bisimilarity is an equivalence in the same way as strong FH-bisimilarity.
+
+In practice, we are dealing with finite representations of the (infinite) open automata.
+In \cite{PEPM}, we defined a slightly modified definition of the ``coverage'' proof obligation, in the case of strong FH-Bisimulation.
+This modification is required to manage in a finite way all possible instantiations of an OT.
+In the case of weak FH-Bisimulation, the proof obligation from definition \ref{def-Weak-bisim} becomes:
+
+ $\forall fv_{OT}. \{ \Pred \land \Pred_{OT}\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
+  \left[\exists fv_{OT_x}.\\
+    \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
+     \!\land\! \alpha\!=\!\alpha_x\! \land\!  
+     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)\right]\}}$
+
+In which $fv_{OT}$ denotes the set of free variables of all expressions in $OT$.
+
+\medskip
+Our first important result is that Weak FH-bisimilarity is an equivalence in the same way as strong FH-bisimilarity:
 
 \begin{theorem}[Weak FH-Bisimulation is an equivalence]\label{thm-weak-equiv} Suppose $\mathcal{R}$ 
-is a weak FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
+is a weak FH-bisimulation. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
 reflexive, symmetric and transitive.
@@
 In the tools, this is managed by the static semantic layer; in the following example, we have renamed all conflicting variables with 1 for the Spec, and 2 for the Impl.
-    \item In practice, we are dealing with finite representations of the (infinite) open automata.
-In \cite{PEPM}, we defined a slightly modified definition of the ``coverage'' proof obligation, in the case of strong FH-Bisimulation.
-This modification is required to manage in a finite way all possible instantiations of an OT.
-In the case of weak FH-Bisimulation, the proof obligation from definition \ref{def-Weak-bisim} becomes:
-
- $\forall fv_{OT}. \{ \Pred \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
-  \left[\exists fv_{OT_x}.\\
-    \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
-     \!\land\! \alpha\!=\!\alpha_x\! \land\!  
-     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)\right]}$
-
     \end{itemize}
 
-  Now consider relation $\mathcal{R}$ defined by the following triples:
+  \medskip
+  Now consider the relation $\mathcal{R}$ defined by the following triples:
 
@@
     \hline
-    b0 & $\ostate{000}$ & True\\
-    b0 & $\ostate{202}$ & True\\
-    b1 & $\ostate{100}$ & $\texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec}$\\
-    b1 & $\ostate{210}$ & $\texttt{b1\_msg = m1\_msg} \land \texttt{b1\_ec = m1\_ec}$\\
-    b1 & $\ostate{220}$ & $\texttt{b1\_msg = m2\_msg} \land \texttt{b1\_ec = m2\_ec}$\\
-    b1 & $\ostate{201}$ & $\texttt{b1\_msg = r1\_msg} \land \texttt{b1\_ec = r1\_ec}$\\
+    b0 & $000$ & True\\
+    b0 & $202$ & True\\
+    b1 & $100$ & $\texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec}$\\
+    b1 & $210$ & $\texttt{b1\_msg = m1\_msg} \land \texttt{b1\_ec = m1\_ec}$\\
+    b1 & $220$ & $\texttt{b1\_msg = m2\_msg} \land \texttt{b1\_ec = m2\_ec}$\\
+    b1 & $201$ & $\texttt{b1\_msg = r1\_msg} \land \texttt{b1\_ec = r1\_ec}$\\
     \hline
@@
 
-  Consider the first triple from the table, and transition $WS_3(n)$ from state $\ostate{b0}$ for some fixed integer $n$. Its easy to guess that it will correspond to $WI_3(n)$ of $\ostate{000}$.
+  \medskip
+  Consider the first triple from the table, and transition $WS_3(n)$ from state $b0$ for some fixed integer $n$. Its easy to guess that it will correspond to $WI_3(n)$ of $000$.
 
   $ WS_3(n) = \openrule
-  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
-    (\texttt{b1\_msg}\gets \texttt{m}, \texttt{b1\_ec}\gets n)}
-  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
+  {\{\texttt{P}\mapsto \texttt{p-send(m1)}\}, True,
+    (\texttt{b1\_msg}\gets \texttt{m1}, \texttt{b1\_ec}\gets n)}
+  {000 \OTWeakarrow {\underline{\texttt{in(m1)}}} 100}
   $
@@
 $ WI_3(n) = \openrule
-  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
-    (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets n)}
-  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
+  {\{\texttt{P}\mapsto \texttt{p-send(m2)}\}, True,
+    (\texttt{s1\_msg}\gets \texttt{m2}, \texttt{s1\_ec}\gets n)}
+  {000 \OTWeakarrow {\underline{\texttt{in(m2)}}} 100}
   $
@@
   \item Their sets of active (non-silent) holes is the same: $\{P\}$.
-  \item Triple ($\ostate{b1},  \ostate{100},  \texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec}$) is in $\mathcal{R}$.
+  \item Triple ($b1,  100,  \texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec}$) is in $\mathcal{R}$.
   \item The verification condition \\
-    $\Pred \land \Pred_{OT}%\\
+    $\forall fv_{OT}. \{ \Pred \land \Pred_{OT}\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
+   \left[\exists fv_{OT_x}.
   \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
      \!\land\! \alpha\!=\!\alpha_x\! \land\!  
-     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}$
+     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)\right]\}}$
 
@@
 
-\TODO{Insert here $\forall \phi(m1,m2)$ }
-
-$True \land True\hspace{1cm} \implies\\ 
-\texttt{p-send(m1)} = \texttt{p-send(m2)}
+$\forall m1. \{True \land True\hspace{3mm} \implies
+\exists m2. \\
+(\texttt{p-send(m1)} = \texttt{p-send(m2)}
 \land True
-\land \underline{\texttt{in(m1)}} = \underline{\texttt{in(m2)}}
+\land \underline{\texttt{in(m1)}} = \underline{\texttt{in(m2)}}\\
 \land (\texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec})
 \subst{(\texttt{b1\_msg}\gets \texttt{m}, \texttt{b1\_ec}\gets n)
-  \uplus (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets n)}
+  \uplus (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets n)})\}
 $
@@
 \land \texttt{in(m1)} = \texttt{in(m2)}
-\land \texttt{m}=\texttt{m} \land n=n)$
+\land \texttt{m1}=\texttt{m2} \land n=n)$
 

### 2020-02-28 2016-Weak-FH-Bisim/WeakBisim.tex
version eric 28/02
Draft 2eme exemple en page 26

@@
 
+  \bigskip
+  Now consider the $3^{rd}$ triple from the table, and transition $WI_{8'}(n)$ from state $100$ to state $000$ for some fixed integer $n$. It should correspond to $WS_7(n)$ of $b1$.
+
+  $ WI_{8'}(n) = \openrule
+         {\{\texttt{Q}\mapsto \texttt{q-recv(s1-msg,s1-ec+n)}\}, True, ()}
+         {100 \OTWeakarrow {\underline{\texttt{out(s1-msg,s1-ec+n)}}} 000}
+         \ \forall n\ge 0$
+
+  $ WS_7(n) = \openrule
+         {\{\texttt{Q}\mapsto \texttt{q-recv(msg,ec+n)}\subst{ec\gets ec+n}\}, True, (ec\gets ec+n)}
+         {b1 \OTWeakarrow {\underline{\texttt{out(msg,ec)}\subst{ec\gets ec+n}}} b0}
+         \ \forall n\ge
+         $
+
+  \medskip       A similar reasonning gives us:
+
+         $\{b1_msg = s1_msg \land b1_ec = s1_ec \land True\hspace{3mm} \implies
+\\
+(\texttt{q-recv(s1-msg,s1-ec+n)} = \texttt{q-recv(msg,ec+n)}
+\land True\\
+\land \underline{\texttt{out(s1-msg,s1-ec+n)}} = {\underline{\texttt{out(msg,ec)}\subst{ec\gets ec+n}}}\\
+\land True \subst{ec\gets ec+n})\}
+$
+
 \section{Related Works}\label{sec:RW}

### 2020-03-04 2016-Weak-FH-Bisim/WeakBisim.tex
mise en coherence, plus gros bug, Figs 1,3,4,7
example comments

@@
 On the top we show the subset of the original open automaton (from Figure \ref{SimpleProtCounter:SpecOA}) considered here, and at the bottom the generated weak transition.
+For reasons of readability, we abbreviate the weak open transitions encoded by $\openrule   {\{\}, True,	() } {s \OTWeakarrow \tau s'}$  as $\texttt{WT}_\tau$.
 The weak open transition shown here is the transition delivering the result of the algorithm to hole $Q$ by applying rules: \WTUn,\WTDeux, and \WTTrois.
@@
 			(\texttt{ec}\gets \texttt{ec}+n) }
-         {\text{b}1 \OTWeakarrow \tau b1} \forall n \geq 0$.  Finally,  applying again \WTTrois, and using the central open transition having \texttt{q-recv(ec)}  as $\alpha$, we get:
-      $\openrule
-         {\{\texttt{Q}\mapsto\texttt{q-revc(ec)}\subst{ec\gets ec+n}\}, True,
-			(\texttt{ec}\gets \texttt{ec}+n) }
-         {b1 \OTWeakarrow {\underline{\texttt{out(m,ec)}}\subst{ec\gets ec+n}} b0} \forall n \geq 0$. 
+         {\text{b}1 \OTWeakarrow \tau b1} \forall n \geq 1$.
+Finally,  applying again \WTTrois, and using the central open transition having \texttt{\underline{out(m,ec)}}  as $\alpha$, we get the resulting weak open transition between b0 and b1 (as shown in Figure \ref{WOT2}).
+ %     $\openrule
+ %        {\{\texttt{Q}\mapsto\texttt{q-revc(ec)}\subst{ec\gets ec+n}\}, True,
+%			(\texttt{ec}\gets \texttt{ec}+n) }
+ %        {b1 \OTWeakarrow {\underline{\texttt{out(m,ec)}}\subst{ec\gets ec+n}} b0} \forall n \geq 0$. 
 \end{example}
@@
     For readability, we did not include the full details of the Implementation weak open transitions in Figure \ref{SimpleProtCounter:ImplOA}, they will appear below.
-    First, we the weak OT loops on state $ostate{000}$ are also present in all other states, we did not repeat them.
+    First, we the weak OT loops on state ${000}$ are also present in all other states, we did not repeat them.
 Then many WOTs are similar, and numbered accordingly as 3, 3', 3'', and 8, 8', 8'',8''' respectively: they only differ by the name of the state variables in their respective source or target states.
@@
 
-$post_4 = (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec})$
-
-$post_5 = (\texttt{m2\_ec}\gets \texttt{m1\_ec})$
-
-$post_6 = (\texttt{s1\_ec}\gets \texttt{m2\_ec+1})$
+$post_4 = (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}, \texttt{s2\_ec}\gets \texttt{s1\_ec})$
+
+$post_5 = ()$
+
+$post_6 = (\texttt{s1\_ec}\gets \texttt{s2\_ec+1})$
 

### 2020-03-04 2016-Weak-FH-Bisim/WeakBisim.tex
details 8'''

--- 2020-02-28 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
-So if we denote ${Post_{456}}^*$ any iteration of this loop, we get ${Post_{456}}^* = (\texttt{s1\_ec}\gets \texttt{s1\_ec}+n)$ for any $n\ge 0$, and we will get e.g.
-the Post of the weak OT number 3' as $ post_4\shortotimes {Post_{456}}^*\shortotimes\ post_3 = (\texttt{m1\_msg}\gets m, \texttt{m1\_ec}\gets n), \forall n\ge 0$
+So if we denote ${Post_{456}}^*$ any iteration of this loop, we get ${Post_{456}}^* = (\texttt{s1\_ec}\gets \texttt{s1\_ec}+n)$ for any $n\ge 0$, and the Post of the weak OT $WI_{3}$ is $ {Post_{456}}^*\shortotimes\ post_3 = (\texttt{s1\_msg}\gets m, \texttt{s1\_ec}\gets n), \forall n\ge 0$ and $Post(WI_{3'})$ is $ post_4\shortotimes {Post_{456}}^*\shortotimes\ post_3 = (\texttt{m1\_msg}\gets m, \texttt{m1\_ec}\gets n), \forall n\ge 0$.
 \medskip
@@
   $ WI_4(n) = \openrule
-         {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n)}
+         {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n, \texttt{s2\_ec}\gets \texttt{s1\_ec}+n)}
          {100 \OTWeakarrow {\tau} 210}
@@
 
-$ WI_8(n) = \openrule
-         {\{\texttt{Q}\mapsto \texttt{q-recv(r1-msg,r1-ec +n)}\}, True, ()}
-         {201 \OTWeakarrow {\underline{\texttt{out(r1-msg,r1-ec +n)}}} 202}
-         \ \forall n\ge 0$
+$Post_{8'''}= post_{8}\shortotimes\ post_{7}\shortotimes\ post_{4}\shortotimes\ Post_{456}^*\shortotimes\ post_{6} = (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_msg}+1+n), \forall n\ge 0$
+
+$ WI_{8'''}(n) = \openrule
+         {\{\texttt{Q}\mapsto \texttt{q-recv(s1\_msg,s2\_ec}+n)\}, True, ()}
+         {210 \OTWeakarrow {\underline{\texttt{out(s1\_msg,s2\_ec+n)}}} 202}
+         \ \forall n\ge 1$
 

### 2020-03-04 2016-Weak-FH-Bisim/WeakBisim.tex
quelques todo dans la derniere annexe
work on abstract

@@
 \begin{abstract}
-  Strong bisimulation allows to compare open systems described using the pNets model.
-  In practice, as happens in process algebras, it is too strong, and
-  we need to define some coarser relations, taking into account
-  invisible or internal moves.
-
+
+Establishing equivalences between programs or system is crucial both for verifying correctness of programs, by establishing that two implementations are equivalent, and for justifying optimisations and program transformations, by establishing that a modified program is equivalent to the source one.
+There exist several equivalence relations for programs, and bisimulations are among the most versatile of these equivalences.
+Among bisimulation relations one distinguishes strong bisimulation, that requires that each action of a program is simulated by a single action of the equivalent program, an weak bisimulations that  is a coarser relations, alowing some of the actions to be
+  invisible or internal moves, and thus not simulated by the equivalent program.
+
+pNets is a generalisation of automata that includes parameters, and hierarchical composition.
+Open pNets are pNets with holes, i.e.
+placeholders inside the hierarchical structure  that can be filled by sub-systems.
+Reasoning on open pNets allows us to reason on open systems.
   Open pNets have a notion of \emph{synchronised actions}
@@
 
-  We use this notion to define an equivalence relation similar to
-  the classical \emph{weak bisimulation}, and study its properties...
+This article defines bisimulation relations for the pNet model, to compare  systems described using the pNets model.
+ We define a strong bisimulation for open pNets.
+  In practice, as happens in process algebras, strong bisimulation is too strong, and
+  we need to define some coarser relations, taking into account
+  invisible or internal moves.
+  We then define an equivalence relation similar to
+  the classical \emph{weak bisimulation}, and study its properties.
 
@@
 
+\TODO{Check coherency, the use-case figures have been modified}
 %% \TODO{keep ?}
@@
 
+\TODO{To be updated completely}
+
 \begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
@@
 
-$ 1 = \openrule
+$ WI_1 = \openrule
 {\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], ()}
 {000 \OTWeakarrow {\tau} 000}$
-
-$ 2 = \openrule
-{\{\texttt{Q}\mapsto \texttt{q-b}\}, [\forall \texttt{m}. \texttt{q-b} \neq \texttt{q-recv(m)} ], ()}
-{000 \OTWeakarrow {\tau} 000}$
-
-$ 3 = \openrule
-  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
-    (\texttt{s1\_msg}\gets m, \texttt{s1\_ec}\gets n)}
-  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
-  \ \forall n\ge 0$
 
@@
   $ WI_4(n) = \openrule
-         {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n)}
+         {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n, \texttt{s2\_ec}\gets \texttt{s1\_ec}+n)}
          {100 \OTWeakarrow {\tau} 210}
          \ \forall n\ge 0$
+
+$Post_{8'''}= post_{8}\shortotimes\ post_{7}\shortotimes\ post_{4}\shortotimes\ Post_{456}^*\shortotimes\ post_{6} = (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_msg}+1+n), \forall n\ge 0$
+
+$ WI_{8'''}(n) = \openrule
+         {\{\texttt{Q}\mapsto \texttt{q-recv(s1\_msg,s2\_ec}+n)\}, True, ()}
+         {210 \OTWeakarrow {\underline{\texttt{out(s1\_msg,s2\_ec+n)}}} 202}
+         \ \forall n\ge 1$
+
+\TODO{no yet checked...:}
+         $ 1 = \openrule
+{\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], ()}
+{000 \OTWeakarrow {\tau} 000}$
+
+$ 2 = \openrule
+{\{\texttt{Q}\mapsto \texttt{q-b}\}, [\forall \texttt{m}. \texttt{q-b} \neq \texttt{q-recv(m)} ], ()}
+{000 \OTWeakarrow {\tau} 000}$
 
@@
          \ \forall n\ge 0$
+
+         \subsection{Details of the Bisimulation Checking}
+         \TODO{To be added}
+
 \end{document}

### 2020-03-05 2016-Weak-FH-Bisim/WeakBisim.tex
Abstract + compositional
signature/affiliation Ludo

@@
 \author{Ludovic Henrio}
+\address{Univ Lyon, EnsL, UCBL, CNRS, Inria,  LIP, F-69342, LYON Cedex 07, France.}
+\email{ludovic.henrio@cnrs.fr}
 
@@
   the classical \emph{weak bisimulation}, and study its properties.
+
+Amon these properties we show compositionality: If two systems are proven equivalent they will be undistinguishable by their context, and they will also be undistinguishable when their holes are filled with equivalent systems.
 

### 2020-03-05 2016-Weak-FH-Bisim/WeakBisim.tex
comments of examples

@@
 
-In \cite{henrio:Forte2016}, we have shown a detailed example of the construction of a complex open transition, building a deduction tree using rules Tr1 and Tr2.
+In \cite{henrio:Forte2016}, we have shown a detailed example of the construction of a complex open transition, building a deduction tree using rules \TrUn and \TrDeux.
 
@@
 In most of the transitions, you can observe that data is propagated between the successive state variables (holding the message, and the error counter value).
-On the right of the figure, you have a loop of $\tau$ actions showing the handling of errors and corresponding increments of the error counter.
+On the right of the figure, you have a loop of $\tau$ actions ($\texttt{OT}_4$, $\texttt{OT}_5$ and $\texttt{OT}_6$)  showing the handling of errors and corresponding increments of the error counter.
 
@@
 On the top we show the subset of the original open automaton (from Figure \ref{SimpleProtCounter:SpecOA}) considered here, and at the bottom the generated weak transition.
-For reasons of readability, we abbreviate the weak open transitions encoded by $\openrule   {\{\}, True,	() } {s \OTWeakarrow \tau s'}$  as $\texttt{WT}_\tau$.
+For reasons of readability, we abbreviate the weak open transitions encoded by $\openrule   {\{\}, True,	() } {s \OTWeakarrow \tau s'}$  as $W_\tau$.
 The weak open transition shown here is the transition delivering the result of the algorithm to hole $Q$ by applying rules: \WTUn,\WTDeux, and \WTTrois.
-First rule \WTUn~ adds an $\texttt{WT}_\tau$ loop on each state.
+First rule \WTUn~ adds an $WT_\tau$ loop on each state.
 Rule \WTDeux~ transforms each 3 OTs into WOTs.
@@
 			(\texttt{ec}\gets \texttt{ec}+n) }
-         {\text{b}1 \OTWeakarrow \tau b1} \forall n \geq 1$.
-Finally,  applying again \WTTrois, and using the central open transition having \texttt{\underline{out(m,ec)}}  as $\alpha$, we get the resulting weak open transition between b0 and b1 (as shown in Figure \ref{WOT2}).
+         {\text{b}1 \OTWeakarrow \tau b1} \forall n \geq 0$.
+Finally,  applying again \WTTrois, and using the central open transition having \texttt{\underline{out(m,ec)}}  as $\alpha$, we get the resulting weak open transition between b1 and b0 (as shown in Figure \ref{WOT2}).
  %     $\openrule
@@
   \begin{example}
-    Figures \ref{SimpleProtCounter:WeakSpecOA} and \ref{SimpleProtCounter:ImplOA} respectively show the weak automata of the simple protocol specification and implementation.
+    Figures \ref{SimpleProtCounter:WeakSpecOA} and \ref{SimpleProtCounter:ImplWOA} respectively show the weak automata of the simple protocol specification and implementation.
+We encode weak open transitions  by $WS$ on the specification model and by $WI$ on the implementation model.
+
     \TODO{comment...}
 
-    For readability, we did not include the full details of the Implementation weak open transitions in Figure \ref{SimpleProtCounter:ImplOA}, they will appear below.
-    First, we the weak OT loops on state ${000}$ are also present in all other states, we did not repeat them.
+    For readability, we did not include the full details of the Implementation weak open transitions in Figure \ref{SimpleProtCounter:ImplWOA}, they will appear below.
+First, we point out that the weak OT loops ($WI_1$,$WI_2$ and $W_\tau$) on state ${000}$ are also present in all other states, we did not repeat them.
 Then many WOTs are similar, and numbered accordingly as 3, 3', 3'', and 8, 8', 8'',8''' respectively: they only differ by the name of the state variables in their respective source or target states.
@@
   \caption{Weak Open Automaton of the implementation}
-   \label{SimpleProtCounter:ImplOA}
+   \label{SimpleProtCounter:ImplWOA}
 \end{figure}

### 2020-03-10 2016-Weak-FH-Bisim/WeakBisim.tex
def subst, et (beta)v

@@
 \author{Eric Madelaine}
-\address{INRIA Sophia Antipolis M\'edit\'erann\'ee, BP 93, 06902 Sophia Antipolis, France}
+\address{INRIA Sophia Antipolis M\'edit\'erann\'ee, UCA, BP 93, 06902 Sophia Antipolis, France}
+\email{eric.madelaine@inria.fr}
 %\date{}                                           % Activate to display a given date or no date
@@
 
-Note that for any term $t$ we have: $t\subst{\Post\shortotimes\Post'} = t\subst{\Post}\subst{\Post'}$
+Note that for any term $t$ we have: $t\subst{\Post\shortotimes\Post'} = (t\subst{\Post})\subst{\Post'}$.\\
+\ERIC{J'ai un probleme ici... quand $Post'$ agit sur des vars de $t$ qui ne sont pas substitutees par $Post$, alors les 2 defs de $\shortotimes$ ci-dessus ne sont pas equivalentes:}\\
+$F(x,z)(\subst{x\gets z}\shortotimes\subst{z\gets 1})=F(x,z)(\subst{x\gets 1})=F(1,z)$\\
+\ERIC{Alors que}\\
+$(F(x,z)\subst{x\gets z})\subst{z\gets 1})=F(z,z)\subst{z\gets 1}=F(1,1)$
+
+\ERIC{Une definition plus correcte serait peut-etre:}\\
+$(x_{k}\gets e_{k})^{k\in K}\shortotimes (x_{k'}\gets e_{k'})^{k'\in K'} =  
+(x_{k}\gets e_{k}\subst{(x_{k'}\gets e_{k'})^{k'\in K'}})^{k\in K} \cup (x_k\gets e_k)^{k\in K'\backslash K}$
 
@@
 By definition, one weak open transition contains  several open transitions, where  each open transition can require an observable action from a given hole, the same hole might have to emit several observable actions for a single weak open transition to occur.
-Consequently, for a weak open transition to trigger, a list of actions from a given hole might be required.
-
+Consequently, for a weak open transition to trigger, a sequence of actions from a given hole may be required.
+
+\TODO{Check, nouvelle formulation, Eric}
 Thus, we let $\gamma$ range over lists of action terms and use $\dotcup$ as the union operator that appends lists of action terms: given two  lists of action terms  $\gamma\dotcup\gamma '$ concatenates the two lists.
-The operation is lifted to indexed sets of lists:  $\set {\gamma_1}\dotcup \set {\gamma_2}$ is an indexed set of lists such that, at each index $i$, $\set {\gamma_1}\dotcup \set {\gamma_2}$ concatenates the list of  actions at index $i$ of $\set{\gamma_1}$ and the one at index $i$ of $\set {\gamma_2}$\footnote{One of the two lists is empty when $i\not \in \dom(\set{\gamma_1})$ or $i\not \in \dom(\set{\gamma_2})$ .}.
+The operation is lifted to indexed sets of lists:  $\set {\gamma_1}\dotcup \set {\gamma_2}$ is an indexed set of lists such that, at each index $i$, $\set {\gamma_1}\dotcup \set {\gamma_2}$ concatenates the list of  actions at index $i$ of $\set{\gamma_1}$ and the one at index $i$ of $\set {\gamma_2}$.
 $[a]$ denotes a list with a single element.
+
+\ERIC{Thus, we let $\gamma$ range over sequences of action terms and use $\dotcup$ as the concatenation operator that appends sequences of action terms: given two sequences of action terms  $\gamma\dotcup\gamma '$ concatenates the two lists.
+The operation is lifted to indexed sets of sequences:  $\set {\gamma_1}\dotcup \set {\gamma_2}$ is an indexed set such that, at each index $i$, $\set {\gamma_1}\dotcup \set {\gamma_2}$ concatenates the sequences of actions at index $i$ of $\set{\gamma_1}$ and the one at index $i$ of $\set {\gamma_2}$\footnote{One of the two sequences is empty when $i\not \in \dom(\set{\gamma_1})$ or $i\not \in \dom(\set{\gamma_2})$ .}.
+$[a]$ denotes a sequence with a single element.}
 
@@
  \[\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}\text{ where }I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}\]
+
+\ERIC{As required actions are now sequences of observable actions, we need an operator to build them from set of (single) hole actions that occur in open transitions.
+Thus we define $\vis{\set\beta}$ as the mapping $\set\beta$  with only observable actions of the holes in $I$, but where each element is either empty or a list of length 1:
+ \[\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}\text{ where }I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}\]}
+
+\ERIC{As an example the $\vis{\set\beta}$ built from the transition $OT_1$ in page \pageref{OT:SimpleProt} is $\texttt{P}\mapsto [\texttt{p-send(m)}]$.
+Remark that in our simple example no $\tau$ transition involves any visible action from a hole, so we have no $\beta$ sequences of length longer than 1 in the weak automaton.}
 

### 2020-03-11 2016-Weak-FH-Bisim/WeakBisim.tex

@@
   \medskip
-  Checking that $\mathcal{R}$ is a weak FH-Bisimulation means checking, for each of these triples, that each WOT of one the states corresponds to a set of WOTs of the other, using the conditions from Definition \ref{def-Weak-bisim}.
+  Checking that $\mathcal{R}$ is a weak FH-Bisimulation means checking, for each of these triples, that each (strong) OT of one the states corresponds to a set of WOTs of the other, using the conditions from Definition \ref{def-Weak-bisim}.
   We give here two examples.
@@
   \medskip
-  Consider the first triple from the table, and transition $WS_3(n)$ from state $b0$ for some fixed integer $n$. Its easy to guess that it will correspond to $WI_3(n)$ of $000$.
-
-  $ WS_3(n) = \openrule
+  Consider the second triple from the table, and transition $SS_3$ from state $b0$. Its easy to guess that it will correspond to $WI_3(0)$ of $202$.
+
+  $ SS_3 = \openrule
   {\{\texttt{P}\mapsto \texttt{p-send(m1)}\}, True,
-    (\texttt{b1\_msg}\gets \texttt{m1}, \texttt{b1\_ec}\gets n)}
-  {000 \OTWeakarrow {\underline{\texttt{in(m1)}}} 100}
+    (\texttt{b1\_msg}\gets \texttt{m1}, \texttt{b1\_ec}\gets 0)}
+  {b0 \OTWeakarrow {\underline{\texttt{in(m1)}}} b1}
   $
 
-$ WI_3(n) = \openrule
+$ WI_3(0) = \openrule
   {\{\texttt{P}\mapsto \texttt{p-send(m2)}\}, True,
-    (\texttt{s1\_msg}\gets \texttt{m2}, \texttt{s1\_ec}\gets n)}
-  {000 \OTWeakarrow {\underline{\texttt{in(m2)}}} 100}
+    (\texttt{s1\_msg}\gets \texttt{m2}, \texttt{s1\_ec}\gets 0)}
+  {202 \OTWeakarrow {\underline{\texttt{in(m2)}}} 100}
   $
@@
 \begin{itemize}
-  \item Their sets of active (non-silent) holes is the same: $\{P\}$.
+  \item Their sets of active (non-silent) holes is the same: $J' = J_x = \{P\}$.
   \item Triple ($b1,  100,  \texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec}$) is in $\mathcal{R}$.
@@
 \exists m2. \\
-(\texttt{p-send(m1)} = \texttt{p-send(m2)}
+(\texttt{[p-send(m1)]} = \texttt{[p-send(m2)]}
 \land True
@@
 \land (\texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec})
-\subst{(\texttt{b1\_msg}\gets \texttt{m}, \texttt{b1\_ec}\gets n)
-  \uplus (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets n)})\}
+\subst{(\texttt{b1\_msg}\gets \texttt{m}, \texttt{b1\_ec}\gets 0)
+  \uplus (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets 0)})\}
 $
@@
 \land \texttt{in(m1)} = \texttt{in(m2)}
-\land \texttt{m1}=\texttt{m2} \land n=n)$
+\land \texttt{m1}=\texttt{m2} \land 0=0)$
 
@@
   \bigskip
-  Now consider the $3^{rd}$ triple from the table, and transition $WI_{8'}(n)$ from state $100$ to state $000$ for some fixed integer $n$. It should correspond to $WS_7(n)$ of $b1$.
-
-  $ WI_{8'}(n) = \openrule
-         {\{\texttt{Q}\mapsto \texttt{q-recv(s1-msg,s1-ec+n)}\}, True, ()}
-         {100 \OTWeakarrow {\underline{\texttt{out(s1-msg,s1-ec+n)}}} 000}
-         \ \forall n\ge 0$
-
-  $ WS_7(n) = \openrule
-         {\{\texttt{Q}\mapsto \texttt{q-recv(msg,ec+n)}\subst{ec\gets ec+n}\}, True, (ec\gets ec+n)}
-         {b1 \OTWeakarrow {\underline{\texttt{out(msg,ec)}\subst{ec\gets ec+n}}} b0}
-         \ \forall n\ge
+  Now consider the $3^{rd}$ triple from the table, and transition $SI_{4}$ from state $100$ to state $210$. It should correspond to $WS_4(0)$ of $b1$, where:
+
+  $ SI_{4} = \openrule
+         {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}, \texttt{s2\_ec}\gets \texttt{s1\_ec})}
+         {100 \OTWeakarrow {\tau} 210}
          $
 
-  \medskip       A similar reasonning gives us:
+  $ WS_4(n) = \openrule
+         {\{\}, True, (b1\_ec\gets b1\_ec+n)}
+         {b1 \OTWeakarrow {\tau} b1}
+         \ \forall n\ge 0
+         $
+
+  \medskip       A similar reasonning gives us\TODO{refaire}
 

### 2020-03-11 2016-Weak-FH-Bisim/WeakBisim.tex
Reponse Eric
small stuff, substitution, refbib foireuses, fon conclusion

@@
 \paragraph{Previous Works and Contribution}
-While most of our previous works relied on closed, fully-instantiated semantics~\cite{BBCHM:article2008,AmeurBoulifa2017,henrio:hal-01303557}, it is only recently that we could design a first version of a  parameterised semantics for pNets with a strong bisimulation equivalence~\cite{henrio:Forte2016}.
+While most of our previous works relied on closed, fully-instantiated semantics~\cite{BBCHM:article2008,AmeurBoulifa2017,HKM-FASE16}, it is only recently that we could design a first version of a  parameterised semantics for pNets with a strong bisimulation equivalence~\cite{henrio:Forte2016}.
 This article builds open this previous parameterised semantics and provide a cleaner version of the semantics with a slightly simplified formalism and extends it to deal with weak bisimulation.
@@
 (x_{k}\gets e_{k}\subst{(x_{k'}\gets e_{k'})^{k'\in K'}})^{k\in K} \cup (x_k\gets e_k)^{k\in K'\backslash K}$
+
+\LUDO{En fait comme on supose qu il y a pas de variable globale et donc que les post doivent affecter toutes les variables ce contre-exemple n est pas applicable!
+apres on peut definir comme ca si on veut ceinture et bretelles mais ca alourdit un peu la definitions}
+
+\ERIC{Non...
+En pratique, dans la composition de posts de la regle WT3, les posts assignent bien toutes les variables de leur OT (strong), mais dans la composition, on fini par avoir des trous...
+Voir page 21-22.
+On est tombes tous les deux separemment, Rabea et moi, sur ce genre de cas.}
 
@@
 In practice, we are dealing with finite representations of the (infinite) open automata.
-In \cite{PEPM}, we defined a slightly modified definition of the ``coverage'' proof obligation, in the case of strong FH-Bisimulation.
+In \cite{hou:hal-02406098}, we defined a slightly modified definition of the ``coverage'' proof obligation, in the case of strong FH-Bisimulation.
 This modification is required to manage in a finite way all possible instantiations of an OT.
@@
 
-This articles defined a strong and a weak bisimulation principles that are adapted to parameterized systems and hierarchical composition.
-Our bisimulation principles handle pNets parameters in the sense that two states might be or not in relation depending on the value of parameters.
+This article defines a strong and a weak bisimulation principles that are adapted to parameterized systems and hierarchical composition.
+Our bisimulation principle handles pNets parameters in the sense that two states might be or not in relation depending on the value of parameters.
 Our strong  bisimulation is compositional by nature in the sense that bisimulation is maintained when composing processes.
@@
 skeletons, or distributed algorithms.
-We have started developping some tool support for computing the
-symbolic semantics in term of open-automata. The following steps will
-be the development of algorithms and tools for checking 
-FH-bisimulations, and interfacing with decision engines for
-predicates, typically SMT solvers. Those tools will include
-an algorithm that partitions the states and generates the right
-conditions (automatically or with user input) for checking
-whether two open pNets are bisimilar.
-
-\TODO{Eric: high level description of the implementation}
+We have developped tool support for computing the
+symbolic semantics in term of open-automata \cite{QBMZ-AVOCS18}, and have
+developed algorithms to check strong FH-bisimulation \cite{hou:hal-02406098}.
 
 \ERIC{
-  =>  citer Avocs et  PEPM\\
-=> Simplification is mostly implemented. It is not strictly required for the Open Automaton construction, but it will be critical later for predicate comparison in the bisimulation algorithm.}
+  =>  Expliquer deux versions algos bisim (check/on-the-fly)\\
+=> Do we need comment on Simplification ? I'm not sure I can write
+something definitive, and Zechen is currently working on it.\\
+=> idees pour implementer Weak efficcement (= sans construire WOA) ?}
+
+\TODO{Further work: Branching ? Refinements ? }
 

### 2020-03-12 2016-Weak-FH-Bisim/WeakBisim.tex
small push

@@
 
-\ERIC{Non...
+\ERIC{Heu Non... 
   En pratique, dans la composition de posts de la regle WT3, les posts assignent bien toutes les variables de leur OT (strong), mais dans la composition, on fini par avoir des trous...
@@
  \[  OT_1  = \openrule{
-      \{\texttt{P}\mapsto \texttt{p-send(m)}\},  [m=m'],  \{s1\_m\gets m\}
+      \{\texttt{P}\mapsto \texttt{p-send(m)}\},  [\texttt{m=m'}],
+        \{\texttt{s1\_m}\gets \texttt{m}\}
                       }
-    {\ostate{s_0,m_0,r_0} \OTarrow{\underline{in(m')}} \ostate{s_1,m_0,r_0}}
+    {\ostate{s_0,m_0,r_0} \OTarrow{\underline{\texttt{in(m')}}} \ostate{s_1,m_0,r_0}}
     \]
@@
     The global states here are triples, build as the product of states of the 3 pLTS (remember the Holes have no state). The assignment
-    $Post$ uses the variable $m$ from the action of hole $P$ to set the
-    value of the sender state variable named $s1\_m$.
+    $Post$ uses the variable $\texttt{m}$ from the action of hole $\texttt{P}$ to set the
+    value of the sender state variable named $\texttt{s1\_m}$.
 
@@
 
-%\subsection{Computing and using open automata}
-%\TODO{REMOVE?  published at Avocs, we can shorten and add a bibref}
-%In this section we present a simple algorithm to construct the open
-%automaton representing the behaviour of an open pNet, and we prove that
-%under reasonable conditions this automaton is finite.
-%
-%\begin{algorithm}[Behavioural semantics of open pNets: Sketch]
-%This is a standard residual algorithm over a set of open-automaton
-%states, but where transitions are open transitions
-%constructively ``proven'' by deduction trees.
-%
-%1) Start with a set of unexplored states containing the initial state
-%of the automaton, and an empty set of explored states.
-%
-%2) While there are unexplored states, pick one state from the
-%unexplored set and add it to the explored set.
-%
-%2a- From this state
-%build all possible deduction trees by application of the structural
-%rules \TrUn\ and \TrDeux, using all applicable combinations
-%of synchronisation vectors.
-%In practice, the algorithm does not explicitely construct the
-%deduction tree, but for each pNet node, builds all possible
-%combinations of the OTs of its subnets, and filter these combinations
-%by matching with all synchronisation vectors. 
-% 
-%2b- For each OT built, add the transition in the
-%outgoing transitions of the current state, and add the
-%resulting state in the unexplored set if it is not already there.
-%
-%3) The predicate is submitted to Z3 for checking satisfiability. If it
-%is NOT satisfiable, the resulting OT is discarded. This will minimize
-%the number of resulting transitions, and by reachability analysis,
-%reduce the resulting open automaton.
-%
-%\end{algorithm}
-
 We have shown in \cite{henrio:Forte2016} that an open-pNet
@@
 \paragraph{Example} Figure \ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the Specification pNet given in Figure \ref{SimpleProt:Spec}. 
-
-%    \begin{figure}[ht]
-  %\centerline{\includegraphics[width=10cm]{ATG/SPImplOpen}}
-%  \caption{Open Automaton of the Simple Protocol Implementation}  %\label{SimpleProtCounter:ImplOA}
-%\end{figure}
+For later references, we give to the transitions of this (strong)
+Specification automaton as $SS_i$ while transitions of the
+Implementation automaton will be labelled $SI_i$. In the figure we
+have annotated each global state with the set of corresponding state variables.
 
@@
 As required actions are now sequences of observable actions, we need an operator to build them from set of actions that occur in open transitions.
-Thus we define $\vis{\set\beta}$ as the mapping $\set\beta$  with only observable actions but where each element is either empty or a list of length 1:
+Thus we define $\vis{\set\beta}$\footnote{\ERIC{La notation
+    $\vis{\beta}$ n'est pas tres parlante, mais je n'ai pas vraiment
+    de meilleure idee...}} as the mapping $\set\beta$  with only observable actions but where each element is either empty or a list of length 1:
  \[\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}\text{ where }I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}\]

### 2020-03-12 2016-Weak-FH-Bisim/WeakBisim.tex
reponse eric

@@
 On est tombes tous les deux separemment, Rabea et moi, sur ce genre de cas.}
+
+\LUDO{euuh ca doit etre lie qu fait qu il manque des ec leftarrowec dans les selfloop de l'OA de spec.
+Plutot que changer la def et les preuves je propose de rajouter la condition $vars(s')=dom(Post)$ pour tous les OAs ce qui ne change rien a part pour les selfloop que l on s autorisait apparemment a ecrire en omettant $x:=x$ ...
+au pire l'identite est un post toujours correct et valide}
 

### 2020-03-12 2016-Weak-FH-Bisim/WeakBisim.tex
check: comments Eric

@@
 \TODO{Check, nouvelle formulation, Eric}
-Thus, we let $\gamma$ range over lists of action terms and use $\dotcup$ as the union operator that appends lists of action terms: given two  lists of action terms  $\gamma\dotcup\gamma '$ concatenates the two lists.
-The operation is lifted to indexed sets of lists:  $\set {\gamma_1}\dotcup \set {\gamma_2}$ is an indexed set of lists such that, at each index $i$, $\set {\gamma_1}\dotcup \set {\gamma_2}$ concatenates the list of  actions at index $i$ of $\set{\gamma_1}$ and the one at index $i$ of $\set {\gamma_2}$.
-$[a]$ denotes a list with a single element.
-
-\ERIC{Thus, we let $\gamma$ range over sequences of action terms and use $\dotcup$ as the concatenation operator that appends sequences of action terms: given two sequences of action terms  $\gamma\dotcup\gamma '$ concatenates the two lists.
+\LUDO{checked, slight changes}
+Thus, we let $\gamma$ range over sequences of action terms and use $\dotcup$ as the concatenation operator that appends sequences of action terms: given two sequences of action terms  $\gamma\dotcup\gamma '$ concatenates the two sequences.
 The operation is lifted to indexed sets of sequences:  $\set {\gamma_1}\dotcup \set {\gamma_2}$ is an indexed set such that, at each index $i$, $\set {\gamma_1}\dotcup \set {\gamma_2}$ concatenates the sequences of actions at index $i$ of $\set{\gamma_1}$ and the one at index $i$ of $\set {\gamma_2}$\footnote{One of the two sequences is empty when $i\not \in \dom(\set{\gamma_1})$ or $i\not \in \dom(\set{\gamma_2})$ .}.
-$[a]$ denotes a sequence with a single element.}
-
-As required actions are now sequences of observable actions, we need an operator to build them from set of actions that occur in open transitions.
-Thus we define $\vis{\set\beta}$\footnote{\ERIC{La notation
-    $\vis{\beta}$ n'est pas tres parlante, mais je n'ai pas vraiment
-    de meilleure idee...}} as the mapping $\set\beta$  with only observable actions but where each element is either empty or a list of length 1:
+$[a]$ denotes a sequence with a single element.
+
+As required actions are now sequences of observable actions, we need an operator to build them from set of actions that occur in open transitions, i.e.
+an operator that takes a set of actions performed by one hole and produces a sequence of observable actions.
+Thus we define $\vis{\set\beta}$ as the mapping $\set\beta$  with only observable actions of the holes in $I$, but where each element is either empty or a list of length 1:
  \[\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}\text{ where }I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}\]
 
-\ERIC{As required actions are now sequences of observable actions, we need an operator to build them from set of (single) hole actions that occur in open transitions.
-Thus we define $\vis{\set\beta}$ as the mapping $\set\beta$  with only observable actions of the holes in $I$, but where each element is either empty or a list of length 1:
- \[\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}\text{ where }I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}\]}
-
-\ERIC{As an example the $\vis{\set\beta}$ built from the transition $OT_1$ in page \pageref{OT:SimpleProt} is $\texttt{P}\mapsto [\texttt{p-send(m)}]$.
-Remark that in our simple example no $\tau$ transition involves any visible action from a hole, so we have no $\beta$ sequences of length longer than 1 in the weak automaton.}
+As an example the $\vis{\set\beta}$ built from the transition $OT_1$ in page \pageref{OT:SimpleProt} is $\texttt{P}\mapsto [\texttt{p-send(m)}]$.
+Remark that in our simple example no $\tau$ transition involves any visible action from a hole, so we have no $\beta$ sequences of length longer than 1 in the weak automaton.
 

### 2020-03-16 2016-Weak-FH-Bisim/WeakBisim.tex
proofreading exampls

@@
 		x_j\!\in\!\vars(s') \right)$. %,  and $s= s'\Rightarrow J=\emptyset$.
+\LUDO{I suggest to add: $\{x_j|j\in J\} = \vars(s')$ or $\{x_j|j\in J\} \cup \iv(\alpha)= \vars(s')$} 
 \end{itemize}
@@
 
-Fig. \ref{SimpleProt:Spec} (left) shows the example principle: two unspecified
+Fig. \ref{SimpleProt:Spec} (left) shows the example principle, which corresponds to the hierarchical structure of a pNet: two unspecified
 processes $P$ and $Q$ (holes) communicate messages, with a data value
 argument, through the two protocol entities.
-Process $P$ send an $\texttt{p-send(m)}$ message to the $Sender$; this communication is denoted as $\texttt{\underline{in(m)}}$, where underline actions represent internal actions (similar to the $\tau$ of CCS), that cannot be further synchronised with the environment.
-At the other end process $Q$ receives the message from the $Receiver$.
+Process $P$ sends an $\texttt{p-send(m)}$ message to the $\symb{Sender}$; this communication is denoted as $\texttt{\underline{in(m)}}$, where underline actions represent internal actions that cannot be further synchronised with the environment, similarly to the $\tau$ of CCS.
+In our formalisation we will also denote these actions $\tau$ for simplicity of notations but the examples are easier to read when invisible actions have significant names.
+At the other end, process $Q$ receives the message from the $\symb{Receiver}$.
 The holes $P$ and $Q$ can also have other interactions with their environment, represented here by actions $\texttt{p-a}$ and $\texttt{q-b}$.
-The underlying network is modelled by a medium entity transporting messages from the sender to the receiver, and that is able to detect transport errors, and signal them to the sender.
-The return $ack$ message from $receiver$ to $sender$ is supposed to be safe.
+The underlying network is modelled by a medium entity transporting messages from the sender to the receiver, and that is able to detect transport errors and signal them to the sender.
+The return $\symb{ack}$ message from $\symb{Receiver}$ to $\symb{Sender}$ is supposed to be safe.
 The final transmission of the message to the recipient (the hole Q) includes the value of the ``error counter'' $ec$.
 
-Fig. \ref{SimpleProt:Spec} (right) shows a graphical view of the pNet of the system \emph{specification}:
+Fig. \ref{SimpleProt:Spec} (right) shows a graphical view of the pNet that specifies the system:
 the full system should be equivalent (e.g. through weak bisimulation)
@@
 It acts as the parallel operator.
-It consists of tree nodes: two Holes $P$ and $Q$ and one subnet, noted {\it PrefectBuffer}.
-Nodes of the tree are synchronized using four synchronization vectors, that  express the possible synchronization between the parameterized actions of a subset of the nodes.
+It consists of three nodes: two Holes $P$ and $Q$ and one subnet, denoted {\it PrefectBuffer}.
+Nodes of the tree are synchronized using four synchronization vectors, that  express the possible synchronizations between the parameterized actions of a subset of the nodes.
 For instance, in the vector "$< \texttt{p-send(m)},\texttt{in(m)},\_> \rightarrow \texttt{\underline{in(m)}}$ only $P$ and {\it PrefectBuffer} nodes are involved in the synchronization.
-More precisely, the synchronization between these processes occurs when  process $P$  performs $\texttt{p-send(m)}$  action sending a message, and  the medium accepts the message through $\texttt{in(m)}$ action  at the same time.
-And the result that will be returned at upper level is the internal action  $\texttt{\underline{in(m)}}$.
+The synchronization between these processes occurs when  process $P$  performs $\texttt{p-send(m)}$  action sending a message, and  the {\it PrefectBuffer} accepts the message through $\texttt{in(m)}$ action  at the same time; the result that will be returned at upper level is the internal action  $\texttt{\underline{in(m)}}$.
 
@@
 \begin{figure}[t]
-   \includegraphics[width=5cm]{XFIG/SimpleProt-Schema}
-   \includegraphics[width=7cm]{XFIG/SimpleProt2-Spec}
-   \caption{Specification pNet Schema and Specification}
+   \includegraphics[width=.37\textwidth]{XFIG/SimpleProt-Schema}
+   \includegraphics[width=.62\textwidth]{XFIG/SimpleProt2-Spec}
+   \caption{pNet structure of the example and specification expressed as a pNet}
    \label{SimpleProt:Spec}
@@
 \begin{figure}[t]
-  \centerline{\includegraphics[width=12cm]{XFIG/SimpleProt2-pNet-tau}}
+  \centerline{\includegraphics[width=.9\textwidth]{XFIG/SimpleProt2-pNet-tau}}
   \caption{Composed pNet with the Simple Protocol Implementation}  \label{SimpleProt:Impl}

### 2020-03-16 2016-Weak-FH-Bisim/WeakBisim.tex
no example again

@@
 \ref{SimpleProt:Impl} shows the pNet model of the protocol implementation.
-When the $Medium$ detects an error (modeled by a local $\tau$ action), it sends back a $\texttt{m\_error}$ message to the $Sender$.
-The $Sender$ increments its local error counter $ec$, and resends the message (including $ec$) to the $Medium$, that will, eventually, transmit $m,ec$ to the $Receiver$.
+When the $\symb{Medium}$ detects an error (modeled by a local $\tau$ action), it sends back a $\texttt{m\_error}$ message to the $\symb{Sender}$.
+The $\symb{Sender}$ increments its local error counter $ec$, and resends the message (including $ec$) to the $\symb{Medium}$, that will, eventually, transmit $m,ec$ to the $\symb{Receiver}$.
+Strictly speaking, as variables are local to each  state, we have two distinct $ec$ variables in the \textit{Sender} pLTS, one in state \texttt{s1}, another one in state \texttt{s2}, the value of the variable is updated along the transitions entering each of the two states.
 

### 2020-03-16 2016-Weak-FH-Bisim/WeakBisim.tex
typo and style example

@@
 %\TODO{Eric: rewrite example with new Protocolkeep only OT1, and adapt comments}
-\begin{example}\emph{An open-transition.}
+\begin{example}[An open-transition]
   \label{OT:SimpleProt}
-At the upper level, the $SimpleSystem$ pNet of Figure \ref{SimpleProt:Impl} has 2 holes and $SimpleProtocol$ as
+At the upper level, the $\symb{SimpleSystem}$ pNet of Figure \ref{SimpleProt:Impl} has 2 holes and $\symb{SimpleProtocol}$ as
 a subnet, itself containing 3 pLTSs. One of its possible open transitions
 (synchronizing the hole $P$
-with the $Sender$ within the \emph{SimpleProtocol}) is:
+with the $\symb{Sender}$ within the \emph{SimpleProtocol}) is:
 

### 2020-03-18 2016-Weak-FH-Bisim/WeakBisim.tex
Update WeakBisim.tex
typos intro,
pour tester GitHub Desktop

@@
 There exist several equivalence relations for programs, and bisimulations are among the most versatile of these equivalences.
-Among bisimulation relations one distinguishes strong bisimulation, that requires that each action of a program is simulated by a single action of the equivalent program, an weak bisimulations that  is a coarser relations, alowing some of the actions to be
+Among bisimulation relations one distinguishes strong bisimulation, that requires that each action of a program is simulated by a single action of the equivalent program, an weak bisimulations that  is a coarser relations, allowing some of the actions to be
   invisible or internal moves, and thus not simulated by the equivalent program.
@@
 Amon these properties we show compositionality: If two systems are proven equivalent they will be undistinguishable by their context, and they will also be undistinguishable when their holes are filled with equivalent systems.
-
-  refinement preorders ?
-
-  Algorithms ?
 
@@
 something definitive, and Zechen is currently working on it.\\
-=> idees pour implementer Weak efficcement (= sans construire WOA) ?}
+=> idees pour implementer Weak efficacement (= sans construire WOA) ?}
 

### 2020-03-18 2016-Weak-FH-Bisim/WeakBisim.tex
discussion skype rabea sur les variables locales et les posts

--- 2020-03-16 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 Note that for any term $t$ we have: $t\subst{\Post\shortotimes\Post'} = (t\subst{\Post})\subst{\Post'}$.\\
-\ERIC{J'ai un probleme ici... quand $Post'$ agit sur des vars de $t$ qui ne sont pas substitutees par $Post$, alors les 2 defs de $\shortotimes$ ci-dessus ne sont pas equivalentes:}\\
-$F(x,z)(\subst{x\gets z}\shortotimes\subst{z\gets 1})=F(x,z)(\subst{x\gets 1})=F(1,z)$\\
-\ERIC{Alors que}\\
-$(F(x,z)\subst{x\gets z})\subst{z\gets 1})=F(z,z)\subst{z\gets 1}=F(1,1)$
-
-\ERIC{Une definition plus correcte serait peut-etre:}\\
-$(x_{k}\gets e_{k})^{k\in K}\shortotimes (x_{k'}\gets e_{k'})^{k'\in K'} =  
-(x_{k}\gets e_{k}\subst{(x_{k'}\gets e_{k'})^{k'\in K'}})^{k\in K} \cup (x_k\gets e_k)^{k\in K'\backslash K}$
-
-\LUDO{En fait comme on supose qu il y a pas de variable globale et donc que les post doivent affecter toutes les variables ce contre-exemple n est pas applicable!
+%\ERIC{J'ai un probleme ici... quand $Post'$ agit sur des vars de $t$ qui ne sont pas substitutees par $Post$, alors les 2 defs de $\shortotimes$ ci-dessus ne sont pas equivalentes:}\\
+%$F(x,z)(\subst{x\gets z}\shortotimes\subst{z\gets 1})=F(x,z)(\subst{x\gets 1})=F(1,z)$\\
+%\ERIC{Alors que}\\
+%$(F(x,z)\subst{x\gets z})\subst{z\gets 1})=F(z,z)\subst{z\gets 1}=F(1,1)$
+%
+%\ERIC{Une definition plus correcte serait peut-etre:}\\
+%$(x_{k}\gets e_{k})^{k\in K}\shortotimes (x_{k'}\gets e_{k'})^{k'\in K'} =  
+%(x_{k}\gets e_{k}\subst{(x_{k'}\gets e_{k'})^{k'\in K'}})^{k\in K} \cup (x_k\gets e_k)^{k\in K'\backslash K}$
+%
+%\LUDO{En fait comme on supose qu il y a pas de variable globale et donc que les post doivent affecter toutes les variables ce contre-exemple n est pas applicable!
 apres on peut definir comme ca si on veut ceinture et bretelles mais ca alourdit un peu la definitions}
-
-\ERIC{Heu Non... 
-  En pratique, dans la composition de posts de la regle WT3, les posts assignent bien toutes les variables de leur OT (strong), mais dans la composition, on fini par avoir des trous...
+%
+%\ERIC{Heu Non... 
+%  En pratique, dans la composition de posts de la regle WT3, les posts assignent bien toutes les variables de leur OT (strong), mais dans la composition, on fini par avoir des trous...
 Voir page 21-22.
 On est tombes tous les deux separemment, Rabea et moi, sur ce genre de cas.}
-
-\LUDO{euuh ca doit etre lie qu fait qu il manque des ec leftarrowec dans les selfloop de l'OA de spec.
+% 
+%\LUDO{euuh ca doit etre lie qu fait qu il manque des ec leftarrowec dans les selfloop de l'OA de spec.
 Plutot que changer la def et les preuves je propose de rajouter la condition $vars(s')=dom(Post)$ pour tous les OAs ce qui ne change rien a part pour les selfloop que l on s autorisait apparemment a ecrire en omettant $x:=x$ ...
@@
 		x_j\!\in\!\vars(s') \right)$. %,  and $s= s'\Rightarrow J=\emptyset$.
-\LUDO{I suggest to add: $\{x_j|j\in J\} = \vars(s')$ or $\{x_j|j\in J\} \cup \iv(\alpha)= \vars(s')$} 
+Additionally we require that: $\{x_j|j\in J\} = \vars(s')$.
+%\LUDO{I suggest to add: $\{x_j|j\in J\} = \vars(s')$ or $\{x_j|j\in J\} \cup \iv(\alpha)= \vars(s')$} 
 \end{itemize}

### 2020-03-21 2016-Weak-FH-Bisim/WeakBisim.tex
appendix and page 22
Added new Figure7 in appendix, and most of the WOTs
Reviewed WOTs in page 22

@@
 {\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], ()}
-{000 \OTWeakarrow {\tau} 000}$
+{S \OTWeakarrow {\texttt{p-a}} S}
+$ (for any state $S$)
 
@@
   {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
-  \ \forall n\ge 0$
+        $($\forall n\ge 0$)
 
 $ WI_4(n) = \openrule
-         {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n, \texttt{s2\_ec}\gets \texttt{s1\_ec}+n)}
+         {\{\}, True, 
+   (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n, \texttt{s2\_ec}\gets \texttt{s1\_ec}+n)}
          {100 \OTWeakarrow {\tau} 210}
-         \ \forall n\ge 0$
-
-$Post_{8'''}= post_{8}\shortotimes\ post_{7}\shortotimes\ post_{4}\shortotimes\ Post_{456}^*\shortotimes\ post_{6} = (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_msg}+1+n), \forall n\ge 0$
-
-$ WI_{8'''}(n) = \openrule
+        $($\forall n\ge 0$)
+
+$ WI_{456}(n) = \openrule
+         {\{\}, True, 
+    (\texttt{s1\_ec}\gets \texttt{s1\_ec}+n)}
+  {100 \OTWeakarrow {\tau} 100}
+        $($\forall n\ge 0$)
+
+$Post_{6a}=\ post_{4}\shortotimes\ Post_{456}^*\shortotimes\ post_{6}\\
+= \left( (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}, \texttt{s2\_ec}\gets \texttt{s1\_ec})
+\shortotimes (\texttt{s1\_ec}\gets \texttt{s1\_ec}+n) \right)
+\shortotimes (\texttt{s1\_ec}\gets \texttt{s2\_ec}+1) \\
+= (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets (\texttt{s2\_ec}+1)+n, \texttt{s2\_ec}\gets (\texttt{s2\_ec}+1)+n)$
+
+$ WI_6a(n) = \openrule
+         {\{\}, True, 
+         (\texttt{m1\_ec}\gets \texttt{s1\_ec}+1+n, \texttt{s2\_ec}\gets \texttt{s2\_ec}+1+n)}
+         {220 \OTWeakarrow {\tau} 210}
+         $($\forall n\ge 0$)
+
+$Post_{8c}= post_{8}\shortotimes\ post_{7}\shortotimes\ post_{4}\shortotimes\ Post_{456}^* 
+= (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_msg}+1+n), \forall n\ge 0$
+
+$ WI_{8c}(n) = \openrule
          {\{\texttt{Q}\mapsto \texttt{q-recv(s1\_msg,s2\_ec}+n)\}, True, ()}
-         {210 \OTWeakarrow {\underline{\texttt{out(s1\_msg,s2\_ec+n)}}} 202}
-         \ \forall n\ge 1$
+         {210 \OTWeakarrow {\underline{\texttt{out(r1\_msg,r1\_ec)}\subst{(\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_msg}+n)}}} 202}
+        $($\forall n\ge 0$)
 
@@
     b1 & $210$ & $\texttt{b1\_msg = m1\_msg} \land \texttt{b1\_ec = m1\_ec}$\\
-    b1 & $220$ & $\texttt{b1\_msg = m2\_msg} \land \texttt{b1\_ec = m2\_ec}$\\
+    b1 & $220$ & $\texttt{b1\_msg = s2\_msg} \land \texttt{b1\_ec = s2\_ec}$\\
     b1 & $201$ & $\texttt{b1\_msg = r1\_msg} \land \texttt{b1\_ec = r1\_ec}$\\
@@
 \begin{figure}[h]
-   \centerline{\includegraphics[width=9cm]{XFIG/SimpleProtImpl-WOA}}
+   \centerline{\includegraphics[width=10cm]{XFIG/SimpleProtImpl-WOA}}
   \caption{Weak Open Automaton of the implementation}
-   \label{Appendix:SpecOA-partial}
+   \label{Appendix:ImplOAl}
 \end{figure}
 
-In Figure \ref{Appendix:SpecOA-partial} we show the weak open automaton of our implementation pNet. Details of the weak transitions is listed here:
+In Figure \ref{Appendix:ImplOA} we show the weak open automaton of our implementation pNet. 
+\TODO{This version is very uncomplete, at least 12 WOTs are missing, inculding: all variants of WI3 starting from 202; the inverse of WI4, WI5, WI6, WI8, etc}
+
+\begin{figure}[h]
+   \centerline{\includegraphics[width=11cm]{XFIG/SimpleProtImpl-WOA2}}
+  \caption{Weak Open Automaton of the implementation: alternative}
+   \label{Appendix:ImplOA2}
+\end{figure}
+
+Figure \ref{Appendix:ImplOA} shows a more compact version of this weak automation, that will be easier to read for humans...
+It is based on the observation that states 202 and 000 are only linked by a "pure $\tau$" transition, and have exactly the same possible behaviors.
+In this configuration we can garanty that they are Weak Bisimilar, and merge their (incoming and outgoing) transitions in the Figure.
+\TODO{May be express this property more formely, but this could be also part of another paper, more oriented towards algorithms and optimisation of the Weak}
+
+\ERIC{Correspondance between the WOTs naming:
+$WI_3 ','',''' -> WI_3 a,b,c$\\
+$WI_7 ','' -> WI_7 a,b$\\
+$WI_8 ','',''' -> WI_8 a,b,c$\\
+$WI_9 ,','' -> W_{456,564,645}$\\
+$WI_{4a,5a,6a}$ are new.
+}
+
+Details of the weak transitions is listed here:
+
+For all global states $S$:
 
@@
 {\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], ()}
-{000 \OTWeakarrow {\tau} 000}$
+{S \OTWeakarrow {\texttt{p-a}} S}$
+
+$ WI_2 = \openrule
+{\{\texttt{Q}\mapsto \texttt{q-b}\}, [\forall \texttt{m,ec}. \texttt{q-b} \neq \texttt{q-recv(m,ec)} ], ()}
+{S \OTWeakarrow {\texttt{q-b}} S}$
+
+All following transitions are parametrized by an arbitrary non-negative integer $n\in \mathcal{N}$:
 
@@
   {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
-  \ \forall n\ge 0$
+$
+
+$ WI_{3a}(n) = \openrule
+  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
+    (\texttt{m1\_msg}\gets \texttt{m}, \texttt{m1\_ec}\gets n), \texttt{s2\_ec}\gets n)}
+  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 210}
+$
+
+$ WI_{3b}(n) = \openrule
+  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
+    (\texttt{s2\_ec}\gets n)}
+  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 220}
+$
+
+$ WI_{3c}(n) = \openrule
+  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
+    (\texttt{r1\_msg}\gets \texttt{m}, \texttt{r1\_ec}\gets n)}
+  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 201}
+$
 
 $ WI_4(n) = \openrule
-         {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n, \texttt{s2\_ec}\gets \texttt{s1\_ec}+n)}
+         {\{\}, True, 
+   (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n, \texttt{s2\_ec}\gets \texttt{s1\_ec}+n)}
          {100 \OTWeakarrow {\tau} 210}
-         \ \forall n\ge 0$
-
-$Post_{8'''}= post_{8}\shortotimes\ post_{7}\shortotimes\ post_{4}\shortotimes\ Post_{456}^*\shortotimes\ post_{6} = (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_msg}+1+n), \forall n\ge 0$
-
-$ WI_{8'''}(n) = \openrule
-         {\{\texttt{Q}\mapsto \texttt{q-recv(s1\_msg,s2\_ec}+n)\}, True, ()}
-         {210 \OTWeakarrow {\underline{\texttt{out(s1\_msg,s2\_ec+n)}}} 202}
-         \ \forall n\ge 1$
-
-\TODO{no yet checked...:}
-         $ 1 = \openrule
-{\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], ()}
-{000 \OTWeakarrow {\tau} 000}$
-
-$ 2 = \openrule
-{\{\texttt{Q}\mapsto \texttt{q-b}\}, [\forall \texttt{m}. \texttt{q-b} \neq \texttt{q-recv(m)} ], ()}
-{000 \OTWeakarrow {\tau} 000}$
-
-$ 5 = \openrule
-         {\{\}, True, (\texttt{m2\_ec}\gets \texttt{m1\_ec}+n)}
+$
+
+$ WI_4a(n) = \openrule
+         {\{\}, True, 
+    (\texttt{s2\_ec}\gets \texttt{s1\_ec}+n)}
+         {100 \OTWeakarrow {\tau} 220}
+$
+
+$ WI_5(n) = \openrule
+         {\{\}, True, (\texttt{s2\_ec}\gets \texttt{s2\_ec}+n)}
          {210 \OTWeakarrow {\tau} 220}
@@
 
-$ 6 = \openrule
-         {\{\}, True, (\texttt{s1\_ec}\gets \texttt{m2\_ec}+n)}
+$ WI_5a(n) = \openrule
+         {\{\}, True, (\texttt{s1\_ec}\gets \texttt{s2\_ec}+1+n)}
+         {210 \OTWeakarrow {\tau} 100}
+         \ \forall n\ge 0$
+
+$ WI_6(n) = \openrule
+         {\{\}, True, (\texttt{s1\_ec}\gets \texttt{s2\_ec}+1+n)}
          {220 \OTWeakarrow {\tau} 100}
@@
 
-$ 7 = \openrule
+$ WI_{456}(n) = \openrule
+         {\{\}, True, 
+    (\texttt{s1\_msg}\gets \texttt{s1\_msg}, \texttt{s1\_ec}\gets \texttt{s1\_ec}+n)}
+  {100 \OTWeakarrow {\tau} 100}
+        $($\forall n\ge 0$)
+
+\TODO{no yet checked (old version), or not yet fully validated ...:}
+
+$ WI_{564}(n) = \openrule
+         {\{\}, True, 
+    (\texttt{m1\_msg}\gets \texttt{m1\_msg}, \texttt{s2\_ec}\gets \texttt{s2\_ec}+1+n, \texttt{m1\_ec}\gets \texttt{s2\_ec}+1+n)}
+  {210 \OTWeakarrow {\tau} 210}
+        $($\forall n\ge 0$)
+
+$ WI_{645}(n) = \openrule
+         {\{\}, True, 
+    (\texttt{s2\_ec}\gets \texttt{s2\_ec}+1+n)}
+  {220 \OTWeakarrow {\tau} 220}
+        $($\forall n\ge 0$)
+
+$ WI_6a(n) = \openrule
+         {\{\}, True, 
+         (\texttt{m1\_ec}\gets \texttt{s1\_ec}+1+n, \texttt{s2\_ec}\gets \texttt{s2\_ec}+1+n)}
+         {220 \OTWeakarrow {\tau} 210}
+         \ \forall n\ge 0$
+
+Because
+
+$Post_{6a}=\ post_{4}\shortotimes\ Post_{456}^*\shortotimes\ post_{6}\\
+= \left( (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}, \texttt{s2\_ec}\gets \texttt{s1\_ec})
+\shortotimes (\texttt{s1\_ec}\gets \texttt{s1\_ec}+n) \right)
+\shortotimes (\texttt{s1\_ec}\gets \texttt{s2\_ec}+1) \\
+= (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets (\texttt{s2\_ec}+1)+n, \texttt{s2\_ec}\gets (\texttt{s2\_ec}+1)+n)$
+
+\medskip
+$ WI_7(n) = \openrule
          {\{\}, True, (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s1\_ec}+n)}
@@
 $ 7'' = \openrule
-         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_ec}\gets \texttt{m2\_ec}+n)}
+         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_ec}+n)}
          {220 \OTWeakarrow {\tau} 201}
+         \ \forall n\ge 1$
+
+$Post_{8'''}= post_{8}\shortotimes\ post_{7}\shortotimes\ post_{4}\shortotimes\ Post_{456}^*\shortotimes\ post_{6} = (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_msg}+1+n), \forall n\ge 0$
+
+$ WI_{8'''}(n) = \openrule
+         {\{\texttt{Q}\mapsto \texttt{q-recv(s1\_msg,s2\_ec}+n)\}, True, ()}
+         {210 \OTWeakarrow {\underline{\texttt{out(s1\_msg,s2\_ec+n)}}} 202}
          \ \forall n\ge 1$

### 2020-03-24 2016-Weak-FH-Bisim/WeakBisim.tex
more WI checked on page 72
Rabea, on a ici 2 "vrai contre exemples", les WI_564* et WI_6a

@@
   {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
-    (\texttt{m1\_msg}\gets \texttt{m}, \texttt{m1\_ec}\gets n), \texttt{s2\_ec}\gets n)}
+    (\texttt{m1\_msg}\gets \texttt{m}, \texttt{m1\_ec}\gets n, \texttt{s2\_ec}\gets n)}
   {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 210}
@@
          {220 \OTWeakarrow {\tau} 100}
-         \ \forall n\ge 0$
-
-$ WI_{456}(n) = \openrule
+         $
+
+$ WI_{456*}(n) = \openrule
          {\{\}, True, 
@@
   {100 \OTWeakarrow {\tau} 100}
-        $($\forall n\ge 0$)
-
-\TODO{no yet checked (old version), or not yet fully validated ...:}
-
-$ WI_{564}(n) = \openrule
+        $
+
+Note that the loop itself does not assign $s1\_msg$, but as we are in a self-loop of state 100, we can add the identity assignment on it.
+\medskip
+
+$ WI_{564*}(n) = \openrule
          {\{\}, True, 
-    (\texttt{m1\_msg}\gets \texttt{m1\_msg}, \texttt{s2\_ec}\gets \texttt{s2\_ec}+1+n, \texttt{m1\_ec}\gets \texttt{s2\_ec}+1+n)}
+    (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{s2\_ec}\gets \texttt{s2\_ec}+1+n, \texttt{m1\_ec}\gets \texttt{s2\_ec}+1+n)}
   {210 \OTWeakarrow {\tau} 210}
-        $($\forall n\ge 0$)
-
-$ WI_{645}(n) = \openrule
+        $
+
+Because
+
+$Post_{564}=\ post_{4}\shortotimes\ post_{6}\shortotimes\ post_{5}\\
+= \left( (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}, \texttt{s2\_ec}\gets \texttt{s1\_ec})
+\shortotimes (\texttt{s1\_ec}\gets \texttt{s2\_ec}+1) \right)
+\shortotimes () \\
+= (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s2\_ec}+1, \texttt{s2\_ec}\gets \texttt{s2\_ec}+1$
+
+This result is INCORRECT: the Post cannot use $s1\_msg$, this variable is not available in state 210
+
+$ WI_{645*}(n) = \openrule
          {\{\}, True, 
@@
   {220 \OTWeakarrow {\tau} 220}
-        $($\forall n\ge 0$)
+        $
 
@@
          {\{\}, True, 
-         (\texttt{m1\_ec}\gets \texttt{s1\_ec}+1+n, \texttt{s2\_ec}\gets \texttt{s2\_ec}+1+n)}
+         (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s2\_ec}+1+n, \texttt{s2\_ec}\gets \texttt{s2\_ec}+1+n)}
          {220 \OTWeakarrow {\tau} 210}
-         \ \forall n\ge 0$
+         $
 
@@
 \medskip
+This result is INCORRECT: the Post cannot use $s1\_msg$, this variable is not available in state 220
+
+The next two  transitions show the same problem, as they include dependencies on $s1\_msg$:
+
+\medskip
 $ WI_7(n) = \openrule
-         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s1\_ec}+n)}
+         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_ec}+n)}
          {100 \OTWeakarrow {\tau} 201}
@@
 
-$ 7' = \openrule
-         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_ec}\gets \texttt{m1\_ec}+n)}
+$ WI_{7a}(n) = \openrule
+         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{m1\_ec}+n)}
          {210 \OTWeakarrow {\tau} 201}
@@
 
-$ 7'' = \openrule
+$ WI_{7b}(n) = \openrule
          {\{\}, True, (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_ec}+n)}
@@
          \ \forall n\ge 1$
+
+\TODO{no yet checked (old version), or not yet fully validated ...:}
 

### 2020-03-27 2016-Weak-FH-Bisim/WeakBisim.tex
developped example in page 26
check, acorrected, and completed use-case in page 26

@@
     (\texttt{b1\_msg}\gets \texttt{m1}, \texttt{b1\_ec}\gets 0)}
-  {b0 \OTWeakarrow {\underline{\texttt{in(m1)}}} b1}
+  {b0 \OTarrow {\underline{\texttt{in(m1)}}} b1}
   $
@@
 \land (\texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec})
-\subst{(\texttt{b1\_msg}\gets \texttt{m}, \texttt{b1\_ec}\gets 0)
-  \uplus (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets 0)})\}
+\subst{(\texttt{b1\_msg}\gets \texttt{m1}, \texttt{b1\_ec}\gets 0)
+  \uplus (\texttt{s1\_msg}\gets \texttt{m2}, \texttt{s1\_ec}\gets 0)})\}
 $
@@
          {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}, \texttt{s2\_ec}\gets \texttt{s1\_ec})}
-         {100 \OTWeakarrow {\tau} 210}
+         {100 \OTarrow {\tau} 210}
          $
@@
   $ WS_4(n) = \openrule
-         {\{\}, True, (b1\_ec\gets b1\_ec+n)}
+         {\{\}, True, (\texttt{b1\_ec}\gets \texttt{b1\_ec}+n)}
          {b1 \OTWeakarrow {\tau} b1}
@@
 
-  \medskip       A similar reasonning gives us\TODO{refaire}
-
-         $\{b1_msg = s1_msg \land b1_ec = s1_ec \land True\hspace{3mm} \implies
-\\
-(\texttt{q-recv(s1-msg,s1-ec+n)} = \texttt{q-recv(msg,ec+n)}
-\land True\\
-\land \underline{\texttt{out(s1-msg,s1-ec+n)}} = {\underline{\texttt{out(msg,ec)}\subst{ec\gets ec+n}}}\\
-\land True \subst{ec\gets ec+n})\}
+  \medskip       A similar reasonning gives us\TODO{Refait, please check. But I think it does not show much more than first case, can we find a better case ?}
+
+\begin{itemize}
+  \item No active holes and the pair of ressulting states $<210,b1>$ is in $\mathcal{R}$.
+\item $fv(SI_4) = \{\}, fv(WS_4(n)) = \{n\}$, \TODO{Is that correct ? Is it true that considering $n$ as a free variable allows Z3 to find  a suitable value...?}
+\item and the verification condition\\
+
+         $(b1_msg = s1_msg \land b1_ec = s1_ec) \land True\hspace{3mm} \implies\\
+\exists n.
+( True \land \tau=\tau
+\land (b1_msg = m1_msg \land b1_ec = m1_ec)  \subst{\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}, \texttt{s2\_ec}\gets \texttt{s1\_ec}}
+\uplus \subst{\texttt{b1\_ec}\gets \texttt{b1\_ec}+n})
 $
+
+is easily proved True for $n=0$.
+ \end{itemize}
 

### 2020-03-27 2016-Weak-FH-Bisim/WeakBisim.tex
corrected states in page 71

@@
 It is based on the observation that states 202 and 000 are only linked by a "pure $\tau$" transition, and have exactly the same possible behaviors.
-In this configuration we can garanty that they are Weak Bisimilar, and merge their (incoming and outgoing) transitions in the Figure.
+In this configuration we can garanty that they are Weak Bisimilar, and merge their (incoming and outgoing) transitions in the Figure. We denote this equivalence class of states as $\{000,202\}$.
 \TODO{May be express this property more formely, but this could be also part of another paper, more oriented towards algorithms and optimisation of the Weak}
@@
 
-All following transitions are parametrized by an arbitrary non-negative integer $n\in \mathcal{N}$:
+All following transitions are parametrized by an arbitrary non-negative integer $n\in \mathcal{N}$.
 
@@
     (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets n)}
-  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
+  { \{000,202\} \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
 $
@@
     (\texttt{m1\_msg}\gets \texttt{m}, \texttt{m1\_ec}\gets n, \texttt{s2\_ec}\gets n)}
-  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 210}
+  { \{000,202\} \OTWeakarrow {\underline{\texttt{in(m)}}} 210}
 $
@@
     (\texttt{s2\_ec}\gets n)}
-  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 220}
+  { \{000,202\} \OTWeakarrow {\underline{\texttt{in(m)}}} 220}
 $
@@
     (\texttt{r1\_msg}\gets \texttt{m}, \texttt{r1\_ec}\gets n)}
-  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 201}
+  { \{000,202\} \OTWeakarrow {\underline{\texttt{in(m)}}} 201}
 $
@@
 
-The next two  transitions show the same problem, as they include dependencies on $s1\_msg$:
-
 \medskip
@@
          {\{\}, True, (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_ec}+n)}
-         {100 \OTWeakarrow {\tau} 201}
+         {210 \OTWeakarrow {\tau} 201}
          \ \forall n\ge 0$
+
+$WI_{7a}$ shows the same problem, as it  includes a dependency on $s1\_msg$:
 
@@
          {\{\}, True, (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{m1\_ec}+n)}
-         {210 \OTWeakarrow {\tau} 201}
+         {220 \OTWeakarrow {\tau} 201}
          \ \forall n\ge 0$
@@
          {\{\}, True, (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_ec}+n)}
-         {220 \OTWeakarrow {\tau} 201}
+         {100 \OTWeakarrow {\tau} 201}
          \ \forall n\ge 1$
@@
 
-         \subsection{Details of the Bisimulation Checking}
-         \TODO{To be added}
+         \subsection{\TODO{Details of the Bisimulation Checking}}
 

### 2020-03-30 2016-Weak-FH-Bisim/WeakBisim.tex
corrections

@@
       \{\texttt{P}\mapsto \texttt{p-send(m)}\},  [\texttt{m=m'}],
-        \{\texttt{s1\_m}\gets \texttt{m}\}
+        \{\texttt{s1\_msg}\gets \texttt{m}\}
                       }
@@
     $Post$ uses the variable $\texttt{m}$ from the action of hole $\texttt{P}$ to set the
-    value of the sender state variable named $\texttt{s1\_m}$.
+    value of the sender state variable named $\texttt{s1\_msg}$.
 
@@
 			(\texttt{ec}\gets \texttt{ec}+1) }
-         {b1 \OTWeakarrow \tau b1}$; $\openrule
+         {\text{b1}\OTWeakarrow \tau \text{b1}}$; $\openrule
          {\{\}, True,
 			(\texttt{ec}\gets \texttt{ec}+1) }
-         {b1 \OTWeakarrow \tau b1}$;  $\openrule
+         {\text{b1} \OTWeakarrow \tau \text{b1}}$;  $\openrule
          {\{\}, True,
 			() }
-         {b1 \OTWeakarrow \tau b1}$. Then Rule \WTTrois~ produces  $\openrule
+         {\text{b1} \OTWeakarrow \tau \text{b1}}$. Then Rule \WTTrois~ produces  $\openrule
          {\{\}, True,
 			(\texttt{ec}\gets \texttt{ec}+2) }
-         {b1 \OTWeakarrow \tau b1}$. We can  can iterate this construction an arbitrary number of times, getting for any natural number $n$ the weak open transition:
+         {\text{b1} \OTWeakarrow \tau \text{b1}}$. We can  can iterate this construction an arbitrary number of times, getting for any natural number $n$ the weak open transition:
   $\openrule
@@
 			(\texttt{ec}\gets \texttt{ec}+n) }
-         {\text{b}1 \OTWeakarrow \tau b1} \forall n \geq 0$.
+         {\text{b1} \OTWeakarrow \tau \text{b1}} \forall n \geq 0$.
 Finally,  applying again \WTTrois, and using the central open transition having \texttt{\underline{out(m,ec)}}  as $\alpha$, we get the resulting weak open transition between b1 and b0 (as shown in Figure \ref{WOT2}).
@@
 
-    \TODO{comment...}
+    \TODO{A lire...}
 
@@
 \end{figure}
+\RAB{In the above example, notations should be corrected once  figure \ref{SimpleProtCounter:ImplWOA} selected}
 
 Now let us give some details about the construction of the weak automaton of the implementation pNet, obtained by application of the weak rules as explained above.
-We concentrate on transitions $WT_3$ and $WT_4$.
+We concentrate on weak open transitions $WI_3$ and $WI_4$.
 Let us denote as $post_n$ the effect (= substitution) of the strong open transitions $OT_n$ from Figure \ref{SimpleProtCounter:ImplOA}:
@@
 
-$post_3 = (\texttt{s1\_ec}\gets 0, \texttt{s1\_m}\gets \texttt{m})$
+$post_3 = (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets 0)$
 
@@
 
-$Post_{456} = post_6 \shortotimes\ post_5 \shortotimes\ post_4
+$post_{456} = post_6 \shortotimes\ post_5 \shortotimes\ post_4
 = (\texttt{s1\_ec}\gets \texttt{s1\_ec}+1)$.
@@
 
-So if we denote ${Post_{456}}^*$ any iteration of this loop, we get ${Post_{456}}^* = (\texttt{s1\_ec}\gets \texttt{s1\_ec}+n)$ for any $n\ge 0$, and the Post of the weak OT $WI_{3}$ is $ {Post_{456}}^*\shortotimes\ post_3 = (\texttt{s1\_msg}\gets m, \texttt{s1\_ec}\gets n), \forall n\ge 0$ and $Post(WI_{3'})$ is $ post_4\shortotimes {Post_{456}}^*\shortotimes\ post_3 = (\texttt{m1\_msg}\gets m, \texttt{m1\_ec}\gets n), \forall n\ge 0$.
+So if we denote ${post_{456}}^*$ any iteration of this loop, we get ${Post_{456}}^* = (\texttt{s1\_ec}\gets \texttt{s1\_ec}+n)$ for any $n\ge 0$, and the Post of the weak OT $WI_{3}$ is $ {Post_{456}}^*\shortotimes\ post_3 = (\texttt{s1\_msg}\gets m, \texttt{s1\_ec}\gets n), \forall n\ge 0$ and $Post(WI_{3'})$ is $ post_4\shortotimes {Post_{456}}^*\shortotimes\ post_3 = (\texttt{m1\_msg}\gets m, \texttt{m1\_ec}\gets n), \forall n\ge 0$.
 \medskip
@@
   {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
-        $($\forall n\ge 0$)
+        $$\forall n\ge 0$
 
@@
          {100 \OTWeakarrow {\tau} 210}
-        $($\forall n\ge 0$)
+        $$\forall n\ge 0$
 
@@
   {100 \OTWeakarrow {\tau} 100}
-        $($\forall n\ge 0$)
+        $$\forall n\ge 0$
 
@@
 
-$ WI_6a(n) = \openrule
+$ WI_{6a}(n) = \openrule
          {\{\}, True, 
@@
     (\texttt{b1\_msg}\gets \texttt{m1}, \texttt{b1\_ec}\gets 0)}
-  {b0 \OTarrow {\underline{\texttt{in(m1)}}} b1}
+  {\text{b0} \OTarrow {\underline{\texttt{in(m1)}}} \text{b1}}
   $
@@
     (\texttt{s1\_msg}\gets \texttt{m2}, \texttt{s1\_ec}\gets 0)}
-  {202 \OTWeakarrow {\underline{\texttt{in(m2)}}} 100}
+  {000 \OTWeakarrow {\underline{\texttt{in(m2)}}} 100}
   $
@@
 \begin{itemize}
-  \item Their sets of active (non-silent) holes is the same: $J' = J_x = \{P\}$.
-  \item Triple ($b1,  100,  \texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec}$) is in $\mathcal{R}$.
+  \item Their sets of active (non-silent) holes is the same: $J' = J_x = \{\texttt{P}\}$.
+  \item Triple ($\text{b1},  100,  \texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec}$) is in $\mathcal{R}$.
   \item The verification condition \\
@@
 
-$\forall m1. \{True \land True\hspace{3mm} \implies
-\exists m2. \\
+$\forall \texttt{m1}. \{True \land True\hspace{3mm} \implies
+\exists \texttt{m2}. \\
 (\texttt{[p-send(m1)]} = \texttt{[p-send(m2)]}
 \land True
-\land \underline{\texttt{in(m1)}} = \underline{\texttt{in(m2)}}\\
-\land (\texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec})
-\subst{(\texttt{b1\_msg}\gets \texttt{m1}, \texttt{b1\_ec}\gets 0)
-  \uplus (\texttt{s1\_msg}\gets \texttt{m2}, \texttt{s1\_ec}\gets 0)})\}
-$
+\land \underline{\texttt{in(m1)}} = \underline{\texttt{in(m2)}} \land 
+\\
+(\texttt{b1\_msg\!\!
+= \!\!s1\_msg} \land \texttt{b1\_ec\!\!
+=\!\!
+s1\_ec}) \subst{(\texttt{b1\_msg}\!\gets\!
+\texttt{m1}, \texttt{b1\_ec}\!\gets\!
+0)\uplus (\texttt{s1\_msg}\!\gets\!
+\texttt{m2},\texttt{s1\_ec}\!\gets\!
+0)})\}$
 
@@
          {\{\}, True, (\texttt{b1\_ec}\gets \texttt{b1\_ec}+n)}
-         {b1 \OTWeakarrow {\tau} b1}
+         {\text{b1} \OTWeakarrow {\tau} \text{b1}}
          \ \forall n\ge 0
@@
 
-         $(b1_msg = s1_msg \land b1_ec = s1_ec) \land True\hspace{3mm} \implies\\
-\exists n.
-( True \land \tau=\tau
-\land (b1_msg = m1_msg \land b1_ec = m1_ec)  \subst{\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}, \texttt{s2\_ec}\gets \texttt{s1\_ec}}
+         $(\texttt{b1\_msg} = \texttt{s1\_msg} \land \texttt{b1\_ec} = \texttt{s1\_ec}) \land True\hspace{3mm} \implies
+\exists n.(True \land \tau=\tau \land \\ (\texttt{b1\_msg} = \texttt{m1\_msg} \land \texttt{b1\_ec} = \texttt{m1\_ec})  \subst{\texttt{m1\_msg}\!\gets\!
+\texttt{s1\_msg}, \texttt{m1\_ec}\!\gets\!
+\texttt{s1\_ec}, \texttt{s2\_ec}\gets \texttt{s1\_ec}}
 \uplus \subst{\texttt{b1\_ec}\gets \texttt{b1\_ec}+n})
@@
 
-$ WI_4a(n) = \openrule
+$ WI_{4a}(n) = \openrule
          {\{\}, True, 
@@
 
-$ WI_5a(n) = \openrule
+$ WI_{5a}(n) = \openrule
          {\{\}, True, (\texttt{s1\_ec}\gets \texttt{s2\_ec}+1+n)}
@@
          \ \forall n\ge 1$
+
+\RAB{Erreur sur les deux transition $WI_{7}$, $WI_{7a}$ et $WI_{7b}$}
 

### 2020-04-01 2016-Weak-FH-Bisim/WeakBisim.tex
pages 72-75
ajoute les WI_8 (mais pas verifie par rapport celles de Biyang)
et ajoute les WI_4P, WI_4Q, WI_456*P a la fin...

@@
   \caption{Weak Open Automaton of the implementation}
-   \label{Appendix:ImplOAl}
+   \label{Appendix:ImplOA}
 \end{figure}
@@
 In Figure \ref{Appendix:ImplOA} we show the weak open automaton of our implementation pNet. 
-\TODO{This version is very uncomplete, at least 12 WOTs are missing, inculding: all variants of WI3 starting from 202; the inverse of WI4, WI5, WI6, WI8, etc}
+\TODO{This version is very uncomplete, at least 12 WOTs are missing, including: all variants of WI3 starting from 202; the inverse of WI4, WI5, WI6, WI8, etc}
+\TODO{See also the last bunch of ransitions, at the end of the list, for combinations of any $\tau$ transition with an external action of P or Q}
 
@@
 
-Figure \ref{Appendix:ImplOA} shows a more compact version of this weak automation, that will be easier to read for humans...
+Figure \ref{Appendix:ImplOA2} shows a more compact version of this weak automation, that will be easier to read for humans...
 It is based on the observation that states 202 and 000 are only linked by a "pure $\tau$" transition, and have exactly the same possible behaviors.
-In this configuration we can garanty that they are Weak Bisimilar, and merge their (incoming and outgoing) transitions in the Figure. We denote this equivalence class of states as $\{000,202\}$.
+More tricky, they do not have the same state variables, as 202 has the variables of state $s2$, but none of these variables are used in transitions from 202.
+In this configuration we can garantee that they are Weak Bisimilar, and merge their (incoming and outgoing) transitions in the Figure. We denote this 
+equivalence class of states as $\{000,202\}$.
 \TODO{May be express this property more formely, but this could be also part of another paper, more oriented towards algorithms and optimisation of the Weak}
 
-\ERIC{Correspondance between the WOTs naming:
-$WI_3 ','',''' -> WI_3 a,b,c$\\
-$WI_7 ','' -> WI_7 a,b$\\
-$WI_8 ','',''' -> WI_8 a,b,c$\\
-$WI_9 ,','' -> W_{456,564,645}$\\
-$WI_{4a,5a,6a}$ are new.
-}
-
 Details of the weak transitions is listed here:
 
-For all global states $S$:
+In the first 3 weak transitions, $S$ denotes the set of all global states.
+
+$ W_\tau = \openrule
+{\{\}, True, ()}
+{S \OTWeakarrow {\tau} S}$
 
@@
 
+$ WI_{6a}(n) = \openrule
+         {\{\}, True, 
+         (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s2\_ec}+1+n, \texttt{s2\_ec}\gets \texttt{s2\_ec}+1+n)}
+         {220 \OTWeakarrow {\tau} 210}
+         $
+
+Because
+
+$Post_{6a}=\ post_{4}\shortotimes\ Post_{456}^*\shortotimes\ post_{6}\\
+= \left( (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}, \texttt{s2\_ec}\gets \texttt{s1\_ec})
+\shortotimes (\texttt{s1\_ec}\gets \texttt{s1\_ec}+n) \right)
+\shortotimes (\texttt{s1\_ec}\gets \texttt{s2\_ec}+1) \\
+= (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets (\texttt{s2\_ec}+1)+n, \texttt{s2\_ec}\gets (\texttt{s2\_ec}+1)+n)$
+
+\medskip
+This result ($WI_{6a}$) is INCORRECT: the Post cannot use $s1\_msg$, this variable is not available in state 220
+
 $ WI_{456*}(n) = \openrule
@@
 
-$ WI_{6a}(n) = \openrule
-         {\{\}, True, 
-         (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s2\_ec}+1+n, \texttt{s2\_ec}\gets \texttt{s2\_ec}+1+n)}
-         {220 \OTWeakarrow {\tau} 210}
-         $
-
-Because
-
-$Post_{6a}=\ post_{4}\shortotimes\ Post_{456}^*\shortotimes\ post_{6}\\
-= \left( (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}, \texttt{s2\_ec}\gets \texttt{s1\_ec})
-\shortotimes (\texttt{s1\_ec}\gets \texttt{s1\_ec}+n) \right)
-\shortotimes (\texttt{s1\_ec}\gets \texttt{s2\_ec}+1) \\
-= (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets (\texttt{s2\_ec}+1)+n, \texttt{s2\_ec}\gets (\texttt{s2\_ec}+1)+n)$
-
-\medskip
-This result is INCORRECT: the Post cannot use $s1\_msg$, this variable is not available in state 220
-
 \medskip
@@
 
-\TODO{no yet checked (old version), or not yet fully validated ...:}
-
-$Post_{8'''}= post_{8}\shortotimes\ post_{7}\shortotimes\ post_{4}\shortotimes\ Post_{456}^*\shortotimes\ post_{6} = (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_msg}+1+n), \forall n\ge 0$
-
-$ WI_{8'''}(n) = \openrule
-         {\{\texttt{Q}\mapsto \texttt{q-recv(s1\_msg,s2\_ec}+n)\}, True, ()}
-         {210 \OTWeakarrow {\underline{\texttt{out(s1\_msg,s2\_ec+n)}}} 202}
+$ WI_8 = \openrule
+         {\{\texttt{Q}\mapsto \texttt{q-recv(r1-msg,r1-ec)}\}, True, ()}
+         {201 \OTWeakarrow {\underline{\texttt{out(r1-msg,r1-ec)}}} \{202, 000\}}
+         \ \forall n\ge 0$
+
+$ WI_{8a}(n) = \openrule
+         {\{\texttt{Q}\mapsto \texttt{q-recv(m1\_msg,m1\_ec}+n)\}, True, ()}
+         {210 \OTWeakarrow {\underline{\texttt{out(m1\_msg,m1\_ec}+n)}} \{202, 000\}}
          \ \forall n\ge 1$
 
-$ WI_8(n) = \openrule
-         {\{\texttt{Q}\mapsto \texttt{q-recv(r1-msg,r1-ec +n)}\}, True, ()}
-         {201 \OTWeakarrow {\underline{\texttt{out(r1-msg,r1-ec +n)}}} 202}
-         \ \forall n\ge 0$
-
-$ WI_9(n) = \openrule
-         {\{\}, True, (\texttt{m1\_ec}\gets \texttt{m1\_ec}+n)}
-         {210 \OTWeakarrow {\tau} 210}
-         \ \forall n\ge 0$
+ $ WI_{8b}(n) = \openrule
+         {\{\texttt{Q}\mapsto \texttt{q-recv(??\_msg,s2\_ec}+n)\}, True, ()}
+         {220 \OTWeakarrow {\underline{\texttt{out(??\_msg,m2\_ec}+n)}} \{202, 000\}}
+         \ \forall n\ge 1$
+
+ $ WI_{8c}(n) = \openrule
+         {\{\texttt{Q}\mapsto \texttt{q-recv(s1\_msg,s1\_ec}+n)\}, True, ()}
+         {100 \OTWeakarrow {\underline{\texttt{out(s1\_msg,s1\_ec}+n)}} \{202, 000\}}
+         \ \forall n\ge 1$
+
+%$Post_{8'''}= post_{8}\shortotimes\ post_{7}\shortotimes\ post_{4}\shortotimes\ Post_{456}^*\shortotimes\ post_{6} = (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_msg}+1+n), \forall n\ge 0$
+
+\medskip
+Then for all $\tau$ transitions above we have a similar WOT that include a non-$\tau$ move from an external action of P or Q, like for example:
+
+$ WI_4P(n) = \openrule
+         {\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], 
+   (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n, \texttt{s2\_ec}\gets \texttt{s1\_ec}+n)}
+         {100 \OTWeakarrow {\texttt{p-a}} 210}
+$
+and
+$ WI_4Q(n) = \openrule
+         {\{\texttt{Q}\mapsto \texttt{q-b}\}, [\forall \texttt{m,ec}. \texttt{q-b} \neq \texttt{q-recv(m,ec)} ],
+   (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n, \texttt{s2\_ec}\gets \texttt{s1\_ec}+n)}
+         {100 \OTWeakarrow {\texttt{q-b}} 210}
+$
+
+but also e.g.:
+
+$ WI_{456*}P(n) = \openrule
+        {\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], 
+    (\texttt{s1\_msg}\gets \texttt{s1\_msg}, \texttt{s1\_ec}\gets \texttt{s1\_ec}+n)}
+  {100 \OTWeakarrow {\texttt{p-a}} 100}
+        $
 

### 2020-04-02 2016-Weak-FH-Bisim/WeakBisim.tex
small modif
dans def 5 et 6, page 10

@@
         represented as a substitution of the form $({x_k\gets e_k})^{k\in K}$ 
-	where $x_k$ are state variables of $s'$, and $e_k$ are expressions
-        over the source variables. Open transitions are identified
+	where $x_k$ are\ \ERIC{the state variables of $s'$}\footnote{all of them, completed by identity if needed}, and $e_k$ are expressions
+        over the \ERIC{source or target state variables}\footnote{On pourrait du coup y mettre ici n'importe quelle variable du OA...}. Open transitions are identified
         modulo logical equivalence on their predicate. 
@@
 
+  \begin{tabular}{|c|c|l|}
+\hline
+    Spec state & Impl state & Predicate\\
+    \hline
+    b0 & $000$ & True\\
+    b0 & $202$ & True\\
+    b1 & $100$ & $\texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec}$\\
+    b1 & $210$ & $\texttt{b1\_msg = m1\_msg} \land \texttt{b1\_ec = m1\_ec}$\\
+    b1 & $220$ & $\texttt{b1\_msg = s2\_msg} \land \texttt{b1\_ec = s2\_ec}$\\
+    b1 & $201$ & $\texttt{b1\_msg = r1\_msg} \land \texttt{b1\_ec = r1\_ec}$\\
+    \hline
+    \end{tabular}
+
 \end{document}

### 2020-04-03 2016-Weak-FH-Bisim/WeakBisim.tex
moved Fig 10, and added D.1
replaced Fig 7 by Fig 10,
added some first content to appendix D.1

@@
 
+%\begin{figure}[h]
+  % \centerline{\includegraphics[width=11cm]{XFIG/SimpleProtImpl-WOA}}
+ % \caption{Weak Open Automaton of the implementation}
+ %  \label{SimpleProtCounter:ImplWOA}
+%\end{figure}
+\RAB{In the above example, notations should be corrected once  figure \ref{SimpleProtCounter:ImplWOA} selected}
+
 \begin{figure}[h]
-   \centerline{\includegraphics[width=11cm]{XFIG/SimpleProtImpl-WOA}}
+   \centerline{\includegraphics[width=11cm]{XFIG/SimpleProtImpl-WOA2}}
   \caption{Weak Open Automaton of the implementation}
-   \label{SimpleProtCounter:ImplWOA}
+   \label{Appendix:ImplOA2}
 \end{figure}
-\RAB{In the above example, notations should be corrected once  figure \ref{SimpleProtCounter:ImplWOA} selected}
 
@@
 
-        \subsection{\TODO{Details of the Bisimulation Checking}}
-
+        \subsection{Details of the Bisimulation Checking}
+
+We reacall here the realtion $\mathcal{R}$ that is the candidate for our weak bisimulation relation:
+
+\bigskip
   \begin{tabular}{|c|c|l|}
@@
 
+\bigskip
+Considering the first triple <b0, 000, True>, we will prove the following properties, in which $OT<<WOT$ means that the (strong) open transition $OT$ is covered, in the sense of definition \ref{def-Weak-bisim} by the weak transition $WOT$ (it could be a set, but this will not be used here):
+
+\bigskip
+$SS_1 << WI_1$
+
+$SS_2 << WI_2$
+
+$SS_3 << WI_3$
+
+\smallskip
+$SI_1 << WS_1$
+
+$SI_2 << WS_2$
+
+$SI_3 << WS_3$
+
+         Note: if we were using the alternative Weak bisim from Appendix \ref{app-WFH-equiv}, Lemma \ref{lem-rel-OT-WOT}, we would have a lot more transitions to examine, as we  have 4 weak transitions for $b0$ in the specification weak automaton, but 7 WOTs from 000 in the implementation automaton.
+
+         And these numbers raise faster for other states, e.g. 13 WOTs for state 100.
+
 \end{document}
-
-%% \section{Examples of Lotos laws}
-%% Possible Lotos small examples:
-
-%% Strong bisim:\\
-%% 1) Hiding:\\
-%% \centerline{hide \{g\} in a;B  ==  a; hide \{g\} in B  iff gatename(a)$\neq$g}\\
-%% \centerline{hide \{g\} in a;B  ==  i; hide \{g\} in B  iff gatename(a)$=$g}
-%% 2) Disabling:\\
-%% \centerline{B1[>(B2[>B3) == (B1[>B2)[>b3}\\
-%% \centerline{(B1[>B2)[]B3 == B1[>B2}\\
-%% \centerline{B[>stop == B}\\
-%% \centerline{stop[>B == B}\\
-%% \centerline{exit(...)[>B == exit(...)[]B}\\
-%% 3) Enabling:\\
-%% \centerline{B1>>(B2>>B3) == (B1>>B2)>>b3}\\
-%% \centerline{B>>stop == B|||stop}\\
-%% \centerline{stop>>B == stop}\\
-%% \centerline{exit>>B == i;B}\\
-%% 4) Choice:\\
-%% \centerline{B1[](B2[]B3) == (B1[]B2)[]b3}\\
-%% \centerline{B1[]B2 == B2[]B1}\\
-%% \centerline{B[]stop == B}\\
-%% \centerline{B[]B == B}\\
-
-%% 5) Others:\\
-%% \centerline{B1|[]|B2 == B1|||B2}\\
-
-%% Weak congruence:\\
-%% \centerline{a;i;B == a;B}\\
-%% \centerline{B[]i;B == i;B}\\
-%% and many others, often not easy to express without syntax for set operations,
-%% like e.g.:
-%% \centerline{}
-
-%% Weak equivalence:\\
-%% \centerline{i;B == B}

### 2020-04-10 2016-Weak-FH-Bisim/WeakBisim.tex
TODOs

@@
 %indexed sets.
+
+\TODO{change composition of post}
 
@@
 
+\TODO{les variables d un automate ou d un plts  cest les variables utilisees dans tous les etats de l automate}
+
 An open automaton is then simply an automaton where each transition is an open transition.
@@
 
+\TODO{switch to variables of open automata instead of state variables + introduce automata}
+
 Let $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$ be a relation over the set $\mathcal{S}_1$ and 
@@
       if $\Pred_{s,t}$       is 
-      \\True, i.e. the states are related when the variables in $s$ and $t$ verify the 
+      True, i.e. the states are related when the variables in $s$ and $t$ verify the 
       predicate $\Pred_{s,t}$.
@@
 A pLTS being its own single leave:
-  $States(\mylangle S,s_0, \to\myrangle) = \{\triangleleft s \triangleright| s \in S\}$.
+  $States(\mylangle S,s_0, \to\myrangle) = \{\triangleleft s \triangleright| s \in S, \}$.
+Formally, the state of a pNet is not reduced to one of its state, it also contains the value of its variables.
+This could be encoded as a mapping from variables of the pNet to expressions, of the form: $\sigma=\{x_i\to e_i\}^{i\in I},\,(x_i\in vars(S))$.
+\LUDO{j ai ajoute les variables mais c est pas tres beau}
 

### 2020-04-14 2016-Weak-FH-Bisim/WeakBisim.tex
TODOs: states, posts and vars in OAs

--- 2020-04-03 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 We use sets of assignments of the form $x_i:=e_i$, ranged over by $\Post$; $\subst{\Post}$ is the substitution that applies all the substitutions defined by $\Post$ in a parallel manner.
-$\otimes$ is the composition operator on substitutions: $(x_k\gets e_k)^{k\in K}\shortotimes \Post =  (x_k\gets e_k\subst{\Post})^{k\in K}$
-
-Note that for any term $t$ we have: $t\subst{\Post\shortotimes\Post'} = (t\subst{\Post})\subst{\Post'}$.\\
+$\otimes$ is the composition operator on substitutions, such that for any term $t$ we have: $t\subst{\Post\shortotimes\Post'} = (t\subst{\Post})\subst{\Post'}$.
+
+For this property to be valid even if the substitution does not operate on all variables,
+we define the composition operation as follows: 
+\TODO{version d eric reprise et corrigee}
+%$(x_k\gets e_k)^{k\in K}\shortotimes \Post =  (x_k\gets e_k\subst{\Post})^{k\in K}$
 %\ERIC{J'ai un probleme ici... quand $Post'$ agit sur des vars de $t$ qui ne sont pas substitutees par $Post$, alors les 2 defs de $\shortotimes$ ci-dessus ne sont pas equivalentes:}\\
@@
 %\ERIC{Une definition plus correcte serait peut-etre:}\\
-%$(x_{k}\gets e_{k})^{k\in K}\shortotimes (x_{k'}\gets e_{k'})^{k'\in K'} =  
-%(x_{k}\gets e_{k}\subst{(x_{k'}\gets e_{k'})^{k'\in K'}})^{k\in K} \cup (x_k\gets e_k)^{k\in K'\backslash K}$
+
+$(x_{k}\gets e_{k})^{k\in K}\shortotimes (x'_{k'}\gets e'_{k'})^{k'\in K'} =  
+(x_{k}\gets e_{k}\subst{(x'_{k'}\gets e'_{k'})^{k'\in K'}})^{k\in K} \cup (x'_{k'}\gets e'_{k'})^{k'\in K''}$\\
+where $K''=\{k'\in K'|x'_{k'}\not\in\{x_k\}^{k\in K}\}$
 %
@@
 
-\begin{definition}[Sorts, Holes, Leaves of pNets]\label{def-sortholeleave}~~
+\begin{definition}[Sorts, Holes, Leaves, Variables of pNets]\label{def-sortholeleave}~~
 
@@
 \]
+
+\item The set of variables of a pNet $P$, denoted $vars(P)$ is the set of variables of all states of all pLTSs that compose $P$.
 
@@
 	An \emph{open automaton} is a structure\\ $A =
-	<J,\mathcal{S},s_0,\mathcal{T}>$ where:
+	<J,\mathcal{S},s_0,V,\mathcal{T}>$ where:
 	\begin{itemize}
@@
 		  among $\mathcal{S}$,
-                  \item[$\bullet$] for each state $s$, $vars(s)=\{v_s\}$ is a set of state variables, and each $v_s$ may have an initial value $init(v_s)$.
+%       \item[$\bullet$] for each state $s$, $vars(s)=\{v_s\}$ is a set of state variables, 
+ \item[$\bullet$] $V$ is a set of variables of the automaton
+		and each $v\in V$ may have an initial value $init(v)$.
 		\item[$\bullet$] $\mathcal{T}$ is a set of open transitions and for each
@@
 
-Let $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$ be a relation over the set $\mathcal{S}_1$ and 
+A relation over the states of two open automata  $<\!J,\mathcal{S}_1, s_0,V_1,
+   \mathcal{T}_1\!>$ and $<\!J,\mathcal{S}_2,V_2,t_0, \mathcal{T}_2\!>$ has the form $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$, it relates states of $\mathcal{S}_1$ and 
 $\mathcal{S}_2$ constrained by a predicate
-More precisely, for any pair $(s,t)$, there is a 
+More precisely, for any pair $(s,t)\in S_1\times S_2$, there is a 
    single
@@
       if $\Pred_{s,t}$       is 
-      \\True, i.e. the states are related when the variables in $s$ and $t$ verify the 
-      predicate $\Pred_{s,t}$.
+      True, i.e. the states are related when the variables in $V_1$ and $V_2$ verify the 
+      predicate $\Pred_{s,t}$. By nature, this is only correctly defines if the variales of the two open automata are disjoint, i.e.  $V_1\cap V_2=\emptyset$.
  FH-bisimulation is defined formally: 
@@
 \begin{minipage}{0.69\linewidth} 	Suppose that
-   $A_1 = <\!J,\mathcal{S}_1, s_0,
-   \mathcal{T}_1\!>$ and $A_2 = <\!J,\mathcal{S}_2,t_0, \mathcal{T}_2\!>$
+   $A_1 = <\!J,\mathcal{S}_1, s_0,V_1,
+   \mathcal{T}_1\!>$ and $A_2 = <\!J,\mathcal{S}_2,V_2,t_0, \mathcal{T}_2\!>$
    are open automata with identical holes of the same sort, with disjoint state variables.
@@
 A pLTS being its own single leave:
-  $States(\mylangle S,s_0, \to\myrangle) = \{\triangleleft s \triangleright| s \in S\}$.
+  $States(\mylangle S,s_0, \to\myrangle) = \{\triangleleft s \triangleright| s \in S, \}$.
+To be precise, the state of a pLTS is not reduced to a state identity, it also contains the value of its variables $vars(P)$.
+%This could be encoded as a mapping from variables of the pNet to expressions, of the form: $\sigma=\{x_i\to e_i\}^{i\in I},\,(x_i\in vars(S))$.
+%\LUDO{j ai ajoute les variables mais c est pas tres beau}
 
@@
 	The semantics of a pNet $\pNet$ is an open automaton $A\!= 
-	<\!\!Holes(\pNet),States(\pNet),InitState(\pNet),\mathcal{T}\!\!>$ where $\mathcal{T}$   is the smallest set of open transitions such that $\mathcal{T}=\{OT\,|\,\pNet \models OT \}$ and	$\pNet \models OT$	is defined by the following  rules:
+	<\!\!Holes(\pNet),States(\pNet),InitState(\pNet),vars(P),\mathcal{T}\!\!>$ where $\mathcal{T}$   is the smallest set of open transitions such that $\mathcal{T}=\{OT\,|\,\pNet \models OT \}$ and	$\pNet \models OT$	is defined by the following  rules:
 %	\begin{itemize}
@@
 \begin{definition}[Non-observability of $\tau$ actions]\label{def:Non-ObsTau}
-An open automaton $A = <J,\mathcal{S},s_0,\mathcal{T}>$ \emph{cannot observe $\tau$ actions} if and only if for all $j$ in $J$ and $s$ in $\mathcal{S}$ we have:
+An open automaton $A = <J,\mathcal{S},s_0,V,\mathcal{T}>$ \emph{cannot observe $\tau$ actions} if and only if for all $j$ in $J$ and $s$ in $\mathcal{S}$ we have:
 \begin{enumerate}
@@
 
-A weak open automaton $<J,\mathcal{S},s_0,\WT>$ is similar to an open automaton  except that $\WT$ is a set of weak open transitions over $J$ and $\mathcal{S}$.
+A weak open automaton $<J,\mathcal{S},s_0,V,\WT>$ is similar to an open automaton  except that $\WT$ is a set of weak open transitions over $J$ and $\mathcal{S}$.
 \end{definition}
@@
 \begin{definition}[Building a weak open automaton]\label{def:buildweakOT}
-  Let $A = <J,\mathcal{S},s_0,\mathcal{T}>$ be an open automaton. 
-The weak open automaton \emph{derived} from $A$ is an open automaton  $<J,\mathcal{S},s_0,\WT>$ where $\WT$ is derived from $\mathcal{T}$ as follows: 
+  Let $A = <J,\mathcal{S},s_0,V,\mathcal{T}>$ be an open automaton. 
+The weak open automaton \emph{derived} from $A$ is an open automaton  $<J,\mathcal{S},s_0,V,\WT>$ where $\WT$ is derived from $\mathcal{T}$ as follows: 
 %\noindent{\bf Invisible $\tau$ transitions:}
@@
 
-\begin{definition}[Weak FH-bisimulation]\label{def-Weak-bisim}
-
+\begin{definition}[Weak FH-bisimulation]\label{def-Weak-bisim} ~\\
 \noindent
-Let $A_1 = <J,\mathcal{S}_1, s_0,
-    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata with disjoint state variables.
-Let $<J,\mathcal{S}_1, s_0,
-    \WT_1>$ and $<J,\mathcal{S}_2,t_0,  \WT_2>$ be the
+Let $A_1 = <J,\mathcal{S}_1, s_0,V_1,
+    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0, V_2, \mathcal{T}_2>$ be open automata with disjoint state variables.
+Let $<J,\mathcal{S}_1, s_0,V_1,
+    \WT_1>$ and $<J,\mathcal{S}_2,t_0, V_2, \WT_2>$ be the
 weak open automata derived from $A_1$ and $A_2$ respectively.
@@
 \begin{lemma}[Alternative definition of weak open transitions]
-\label{lem-rel-OT-WOT} Let $A = <J,\mathcal{S}, s_0,
-    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,
+\label{lem-rel-OT-WOT} Let $A = <J,\mathcal{S}, s_0,V_1,
+    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,V_2,
     \WT>$ be the

### 2020-04-17 2016-Weak-FH-Bisim/WeakBisim.tex
in and out made visible...
J'ai change les \underline{in|out} partout dans le texte.
Rabea, pourra-tu le faire dans les figures ? (c'ets dans toutes sauf la 7 ....)

@@
 \usepackage{macrospNets}
+
+\newcommand{\nounderline}[1]{#1}
 
@@
 
+\TODO{J'ai change les $\underline{in}$ et $\underline{out}$ en $in$ et $out$ dans le texte. Rabea, peux-tu le faire dans toutes les figures (1, 2, 3,4,5,6) ?}
+
 Fig. \ref{SimpleProt:Spec} (left) shows the example principle, which corresponds to the hierarchical structure of a pNet: two unspecified
@@
 argument, through the two protocol entities.
-Process $P$ sends an $\texttt{p-send(m)}$ message to the $\symb{Sender}$; this communication is denoted as $\texttt{\underline{in(m)}}$, where underline actions represent internal actions that cannot be further synchronised with the environment, similarly to the $\tau$ of CCS.
-In our formalisation we will also denote these actions $\tau$ for simplicity of notations but the examples are easier to read when invisible actions have significant names.
+Process $P$ sends an $\texttt{p-send(m)}$ message to the $\symb{Sender}$; this communication is denoted as $\texttt{\nounderline{in(m)}}$% , where underline actions represent internal actions that cannot be further synchronised with the environment, similarly to the $\tau$ of CCS.
+In our formalisation we will also denote these actions $\tau$ for simplicity of notations but the examples are easier to read when invisible actions have significant names}
+.
 At the other end, process $Q$ receives the message from the $\symb{Receiver}$.
@@
 Nodes of the tree are synchronized using four synchronization vectors, that  express the possible synchronizations between the parameterized actions of a subset of the nodes.
-For instance, in the vector "$< \texttt{p-send(m)},\texttt{in(m)},\_> \rightarrow \texttt{\underline{in(m)}}$ only $P$ and {\it PrefectBuffer} nodes are involved in the synchronization.
-The synchronization between these processes occurs when  process $P$  performs $\texttt{p-send(m)}$  action sending a message, and  the {\it PrefectBuffer} accepts the message through $\texttt{in(m)}$ action  at the same time; the result that will be returned at upper level is the internal action  $\texttt{\underline{in(m)}}$.
+For instance, in the vector "$< \texttt{p-send(m)},\texttt{in(m)},\_> \rightarrow \texttt{\nounderline{in(m)}}$" only $P$ and {\it PrefectBuffer} nodes are involved in the synchronization.
+The synchronization between these processes occurs when  process $P$  performs $\texttt{p-send(m)}$  action sending a message, and  the {\it PrefectBuffer} accepts the message through $\texttt{in(m)}$ action  at the same time; the result that will be returned at upper level is the action  $\texttt{\nounderline{in(m)}}$.
 
@@
                       }
-    {\ostate{s_0,m_0,r_0} \OTarrow{\underline{\texttt{in(m')}}} \ostate{s_1,m_0,r_0}}
+    {\ostate{s_0,m_0,r_0} \OTarrow{\nounderline{\texttt{in(m')}}} \ostate{s_1,m_0,r_0}}
     \]
@@
  %%                      }
- %%    {\ostate{s_1,m_0,r_0} \OTarrow{\underline{send(SV2\_m)}} \ostate{s_2,m_1,r_0}}
+ %%    {\ostate{s_1,m_0,r_0} \OTarrow{\nounderline{send(SV2\_m)}} \ostate{s_2,m_1,r_0}}
  %%    $
@@
  %%                      }
- %%    {\ostate{s_1,m_0,r_0} \OTarrow{\underline{send(s_1\_m)}} \ostate{s_2,m_1,r_0}}
+ %%    {\ostate{s_1,m_0,r_0} \OTarrow{\nounderline{send(s_1\_m)}} \ostate{s_2,m_1,r_0}}
  %%    $
@@
 %%   open transition $OT_2$ of \texttt{EnableCompL} (see example page \pageref{OT:ABP-composed}).
-%%   The rule uses \TrUn\ for the $\delta$ transition of $C_3$, for the $l$ transition of $C_4$, then combines the result using the $a_4$ vector of the bottom pNet node, and the $\underline{\delta(x)}$ vector of the top node.
+%%   The rule uses \TrUn\ for the $\delta$ transition of $C_3$, for the $l$ transition of $C_4$, then combines the result using the $a_4$ vector of the bottom pNet node, and the $\nounderline{\delta(x)}$ vector of the top node.
 
@@
          {\text{b1} \OTWeakarrow \tau \text{b1}} \forall n \geq 0$.
-Finally,  applying again \WTTrois, and using the central open transition having \texttt{\underline{out(m,ec)}}  as $\alpha$, we get the resulting weak open transition between b1 and b0 (as shown in Figure \ref{WOT2}).
+Finally,  applying again \WTTrois, and using the central open transition having \texttt{\nounderline{out(m,ec)}}  as $\alpha$, we get the resulting weak open transition between b1 and b0 (as shown in Figure \ref{WOT2}).
  %     $\openrule
@@
 %			(\texttt{ec}\gets \texttt{ec}+n) }
- %        {b1 \OTWeakarrow {\underline{\texttt{out(m,ec)}}\subst{ec\gets ec+n}} b0} \forall n \geq 0$. 
+ %        {b1 \OTWeakarrow {\nounderline{\texttt{out(m,ec)}}\subst{ec\gets ec+n}} b0} \forall n \geq 0$. 
 \end{example}
@@
     (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets n)}
-  {000 \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
+  {000 \OTWeakarrow {\nounderline{\texttt{in(m)}}} 100}
         $$\forall n\ge 0$
@@
          {\{\texttt{Q}\mapsto \texttt{q-recv(s1\_msg,s2\_ec}+n)\}, True, ()}
-         {210 \OTWeakarrow {\underline{\texttt{out(r1\_msg,r1\_ec)}\subst{(\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_msg}+n)}}} 202}
+         {210 \OTWeakarrow {\nounderline{\texttt{out(r1\_msg,r1\_ec)}\subst{(\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_msg}+n)}}} 202}
         $($\forall n\ge 0$)
@@
     (\texttt{b1\_msg}\gets \texttt{m1}, \texttt{b1\_ec}\gets 0)}
-  {\text{b0} \OTarrow {\underline{\texttt{in(m1)}}} \text{b1}}
+  {\text{b0} \OTarrow {\nounderline{\texttt{in(m1)}}} \text{b1}}
   $
@@
     (\texttt{s1\_msg}\gets \texttt{m2}, \texttt{s1\_ec}\gets 0)}
-  {000 \OTWeakarrow {\underline{\texttt{in(m2)}}} 100}
+  {000 \OTWeakarrow {\nounderline{\texttt{in(m2)}}} 100}
   $
@@
 \land True
-\land \underline{\texttt{in(m1)}} = \underline{\texttt{in(m2)}} \land 
+\land \nounderline{\texttt{in(m1)}} = \nounderline{\texttt{in(m2)}} \land 
 \\
@@
     (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets n)}
-  { \{000,202\} \OTWeakarrow {\underline{\texttt{in(m)}}} 100}
+  { \{000,202\} \OTWeakarrow {\nounderline{\texttt{in(m)}}} 100}
 $
@@
     (\texttt{m1\_msg}\gets \texttt{m}, \texttt{m1\_ec}\gets n, \texttt{s2\_ec}\gets n)}
-  { \{000,202\} \OTWeakarrow {\underline{\texttt{in(m)}}} 210}
+  { \{000,202\} \OTWeakarrow {\nounderline{\texttt{in(m)}}} 210}
 $
@@
     (\texttt{s2\_ec}\gets n)}
-  { \{000,202\} \OTWeakarrow {\underline{\texttt{in(m)}}} 220}
+  { \{000,202\} \OTWeakarrow {\nounderline{\texttt{in(m)}}} 220}
 $
@@
     (\texttt{r1\_msg}\gets \texttt{m}, \texttt{r1\_ec}\gets n)}
-  { \{000,202\} \OTWeakarrow {\underline{\texttt{in(m)}}} 201}
+  { \{000,202\} \OTWeakarrow {\nounderline{\texttt{in(m)}}} 201}
 $
@@
          {\{\texttt{Q}\mapsto \texttt{q-recv(r1-msg,r1-ec)}\}, True, ()}
-         {201 \OTWeakarrow {\underline{\texttt{out(r1-msg,r1-ec)}}} \{202, 000\}}
+         {201 \OTWeakarrow {\nounderline{\texttt{out(r1-msg,r1-ec)}}} \{202, 000\}}
          \ \forall n\ge 0$
@@
          {\{\texttt{Q}\mapsto \texttt{q-recv(m1\_msg,m1\_ec}+n)\}, True, ()}
-         {210 \OTWeakarrow {\underline{\texttt{out(m1\_msg,m1\_ec}+n)}} \{202, 000\}}
+         {210 \OTWeakarrow {\nounderline{\texttt{out(m1\_msg,m1\_ec}+n)}} \{202, 000\}}
          \ \forall n\ge 1$
@@
          {\{\texttt{Q}\mapsto \texttt{q-recv(??\_msg,s2\_ec}+n)\}, True, ()}
-         {220 \OTWeakarrow {\underline{\texttt{out(??\_msg,m2\_ec}+n)}} \{202, 000\}}
+         {220 \OTWeakarrow {\nounderline{\texttt{out(??\_msg,m2\_ec}+n)}} \{202, 000\}}
          \ \forall n\ge 1$
@@
          {\{\texttt{Q}\mapsto \texttt{q-recv(s1\_msg,s1\_ec}+n)\}, True, ()}
-         {100 \OTWeakarrow {\underline{\texttt{out(s1\_msg,s1\_ec}+n)}} \{202, 000\}}
+         {100 \OTWeakarrow {\nounderline{\texttt{out(s1\_msg,s1\_ec}+n)}} \{202, 000\}}
          \ \forall n\ge 1$

### 2020-04-17 2016-Weak-FH-Bisim/WeakBisim.tex
quelques TODO en plus
en pages 19 et 84, sur les \gamma de longueur >1

@@
 \item A resulting weak bisimulation equivalence for open pNets and a simple static condition on synchronisation vectors inside pNets that is sufficient to ensure that weak bisimulation is compositional.
-\item An illustrative example \TODO{TODO}
+\item An illustrative example based on a simple transport protocol, showing the construction of the weak open transitions, and the proof of weak bisimulation.
 \end{itemize}
@@
 an operator that takes a set of actions performed by one hole and produces a sequence of observable actions.
+\TODO{Ca serai tpas mal de trouver une notation plus intuitive au lieu de ce $\vis{\set\beta}$ ?}
 Thus we define $\vis{\set\beta}$ as the mapping $\set\beta$  with only observable actions of the holes in $I$, but where each element is either empty or a list of length 1:
@@
 Remark that in our simple example no $\tau$ transition involves any visible action from a hole, so we have no $\beta$ sequences of length longer than 1 in the weak automaton.
+\TODO{en fait c'est faux ! les boucles SS\_1, SS\_2, WS\_1, WS\_2 sont aussi valides avec p\_a ou q\_b = tau, donc on peut avoir des sequences de longueur arbitraire d'actions de P et de Q}
 
@@
 
+\TODO{ajouter les boucles de $WI_1$ et $WI_2$, dans le cas ou $p_a$ (resp $q_b$) sont des $\tau$:}
+
+$WI_{12*}(n) = \openrule
+{\{(\texttt{P}\mapsto \tau|\texttt{Q}\mapsto \tau)^n\},true, ()}
+  {s \OTWeakarrow {\tau} s} 
+s \in S$
+
         \subsection{Details of the Bisimulation Checking}

### 2020-04-17 2016-Weak-FH-Bisim/WeakBisim.tex
relecture

--- 2020-04-14 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 \DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
-\usepackage{epsfig,color,subfigure,enumitem}
+\usepackage{epsfig,color,subfigure,enumitem,soul}
 \newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
@@
 		x_j\!\in\!\vars(s') \right)$. %,  and $s= s'\Rightarrow J=\emptyset$.
-Additionally we require that: $\{x_j|j\in J\} = \vars(s')$.
+\hl{Additionally we require that:} $\{x_j|j\in J\} = \vars(s')$.
 %\LUDO{I suggest to add: $\{x_j|j\in J\} = \vars(s')$ or $\{x_j|j\in J\} \cup \iv(\alpha)= \vars(s')$} 
@@
 A pNet $\pNet$ is a hierarchical structure where leaves are pLTSs and holes:\\
-$\pNet,\pNetQ\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in 
+$\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in 
 K}\myrangle$
@@
   synchronisation vectors. $\forall k\!\in\! K,
-  \symb{SV}_k\!=\!\SV{\alpha_{l}^{l\in I_k \uplus J_k}}{\alpha'_k}{e_k}$ where
+  \symb{SV}_k\!=\!\SV{\alpha_{l}^{l\in I_k \uplus J_k}}{\alpha'_k}{e_k}$ \hl{where}
   $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
@@
  The open transition is itself a logical implication, but using a simple logic (this logic includes the boolean expressions $\AlgB$, boolean operators, and term equality).
-We differentiate classical (black) inference rules that use
- an expressive logic and are paper rules from open transition rules that use a simpler 
- logic, 
- will be embedded into automata transitions, and could typically be handled in a 
- mechanical way.
+\hl{We differentiate classical (black) inference rules that use  an expressive logic and are paper rules from open transition rules that use a simpler  logic,  will be embedded into automata transitions, and could typically be handled in a
+ mechanical way.}
 
@@
 A relation over the states of two open automata  $<\!J,\mathcal{S}_1, s_0,V_1,
-   \mathcal{T}_1\!>$ and $<\!J,\mathcal{S}_2,V_2,t_0, \mathcal{T}_2\!>$ has the form $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$, it relates states of $\mathcal{S}_1$ and 
+   \mathcal{T}_1\!>$ and $<\!J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2\!>$ has the form $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$, it relates states of $\mathcal{S}_1$ and 
 $\mathcal{S}_2$ constrained by a predicate
@@
  \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim} ~\\
-
 \noindent
@@
    $A_1 = <\!J,\mathcal{S}_1, s_0,V_1,
-   \mathcal{T}_1\!>$ and $A_2 = <\!J,\mathcal{S}_2,V_2,t_0, \mathcal{T}_2\!>$
+   \mathcal{T}_1\!>$ and $A_2 = <\!J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2\!>$
    are open automata with identical holes of the same sort, with disjoint state variables.
@@
 $\Post_{OT_x}$ that are independent), applying the assignments of the involved rules.
-We can prove that such a bisimulation si an equivalence relation:
+We can prove that such a bisimulation is an equivalence relation:
 
@@
 of two relations with predicate is defined; this is not exactly
-standard as it necessitates to define the right predicate for the
+standard as it requires to define the right predicate for the
 transitive composition and producing a single predicate to relate any
@@
 the predicates inclusion is decidable over  
-the action algebra $\mathcal{A}_P$. Then it is decidable whether the relation 
+\hl{the action algebra} $\mathcal{A}_P$. Then it is decidable whether the relation 
 $\mathcal{R}$ is a FH-bisimulation.
@@
 	\label{def:operationalSemantics}
-	The semantics of a pNet $\pNet$ is an open automaton $A\!= 
+\hl{The semantics of a pNet} $\pNet$ is an open automaton $A\!= 
 	<\!\!Holes(\pNet),States(\pNet),InitState(\pNet),vars(P),\mathcal{T}\!\!>$ where $\mathcal{T}$   is the smallest set of open transitions such that $\mathcal{T}=\{OT\,|\,\pNet \models OT \}$ and	$\pNet \models OT$	is defined by the following  rules:
@@
 	synchronisation vector (of index $k$) applicable to the rule subject, the premisses
-	include one {\em open transition} for each sub-pNet involved , one possible
+	include one {\em open transition} for each sub-pNet involved, one possible
 	{\em action} for each Hole involved, and the predicate relating these
@@
 
-In \cite{henrio:Forte2016}, we have shown a detailed example of the construction of a complex open transition, building a deduction tree using rules \TrUn and \TrDeux.
+In \cite{henrio:Forte2016}, we have shown a detailed example of the construction of a complex open transition, building a deduction tree using rules \TrUn ~and \TrDeux.
 
@@
 \begin{figure}[ht]
-   \centerline{\includegraphics[width=12cm]{XFIG/SPSpecOpen}}
+   \centerline{\includegraphics[width=13cm]{XFIG/SPSpecOpen}}
    \caption{Specification OA}
@@
 
-\paragraph{Example} Figure \ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the Specification pNet given in Figure \ref{SimpleProt:Spec}. 
+\paragraph{Example} \hl{Figure} \ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the Specification pNet given in Figure \ref{SimpleProt:Spec}. 
 For later references, we give to the transitions of this (strong)
@@
 synchronisation with their context.
-The notions of non-observable action varies in different contexts,
+The notion of non-observable actions varies in different contexts,
 e.g. $tau$ in CCS, and $i$ in Lotos, we could define classically a set of
@@
 \begin{figure}[ht]
-   \centerline{\includegraphics[width=10cm]{XFIG/WOT2-result}}
+   \centerline{\includegraphics[width=12cm]{XFIG/WOT2-result}}
   \caption{Construction of an example of weak open transition}
@@
          {\text{b1} \OTWeakarrow \tau \text{b1}} \forall n \geq 0$.
-Finally,  applying again \WTTrois, and using the central open transition having \texttt{\underline{out(m,ec)}}  as $\alpha$, we get the resulting weak open transition between b1 and b0 (as shown in Figure \ref{WOT2}).
+Finally,  applying again \WTTrois, and using the central open transition having \texttt{\underline{out(b1\_m,b1\_ec)}}  as $\alpha$, we get the resulting weak open transition between b1 and b0 (as shown in Figure \ref{WOT2}).
  %     $\openrule
@@
   \begin{example}
-    Figures \ref{SimpleProtCounter:WeakSpecOA} and \ref{SimpleProtCounter:ImplWOA} respectively show the weak automata of the simple protocol specification and implementation.
+    Figures \ref{SimpleProtCounter:WeakSpecOA} and \ref{SimpleProtCounter:ImplWOA2} respectively show the weak automata of the simple protocol specification and implementation.
 We encode weak open transitions  by $WS$ on the specification model and by $WI$ on the implementation model.
-
-    \TODO{A lire...}
-
-    For readability, we did not include the full details of the Implementation weak open transitions in Figure \ref{SimpleProtCounter:ImplWOA}, they will appear below.
-First, we point out that the weak OT loops ($WI_1$,$WI_2$ and $W_\tau$) on state ${000}$ are also present in all other states, we did not repeat them.
-Then many WOTs are similar, and numbered accordingly as 3, 3', 3'', and 8, 8', 8'',8''' respectively: they only differ by the name of the state variables in their respective source or target states.
-\end{example}
 
@@
 
+ For readability, we did not include the full details of the Implementation weak open transitions in Figure \ref{SimpleProtCounter:ImplWOA2}, they will appear below.
+First, we point out that the weak OT loops ($WI_1$,$WI_2$ and $W_\tau$) on state ${000}$ are also present in all other states, we did not repeat them.
+Then many WOTs are similar, and numbered accordingly as 3, 3a, 3b, 3c and 8, 8a, 8b, 8c respectively: they only differ by the name of the state variables in their respective source or target states.
+\end{example}
+
 %\begin{figure}[h]
@@
 %\end{figure}
-\RAB{In the above example, notations should be corrected once  figure \ref{SimpleProtCounter:ImplWOA} selected}
 
@@
   \caption{Weak Open Automaton of the implementation}
-   \label{Appendix:ImplOA2}
+   \label{SimpleProtCounter:ImplWOA2}
 \end{figure}
@@
 
-So if we denote ${post_{456}}^*$ any iteration of this loop, we get ${Post_{456}}^* = (\texttt{s1\_ec}\gets \texttt{s1\_ec}+n)$ for any $n\ge 0$, and the Post of the weak OT $WI_{3}$ is $ {Post_{456}}^*\shortotimes\ post_3 = (\texttt{s1\_msg}\gets m, \texttt{s1\_ec}\gets n), \forall n\ge 0$ and $Post(WI_{3'})$ is $ post_4\shortotimes {Post_{456}}^*\shortotimes\ post_3 = (\texttt{m1\_msg}\gets m, \texttt{m1\_ec}\gets n), \forall n\ge 0$.
+So if we denote ${post_{456*}}$ any iteration of this loop, we get ${post_{456*}} = (\texttt{s1\_ec}\gets \texttt{s1\_ec}+n)$ for any $n\ge 0$, and the \Post~ of the weak OT  $WI_{3}$ is:\\
+ ${post_{456*}}\shortotimes\ post_3 = (\texttt{s1\_msg}\gets m, \texttt{s1\_ec}\gets n), \forall n\ge 0$ and \Post~ of  $WI_{3a}$  is:\\ $post_4\shortotimes {post_{456*}}\shortotimes\ post_3 = (\texttt{m1\_msg}\gets m, \texttt{m1\_ec}\gets n), \forall n\ge 0$.
 \medskip
 
-We can now show some of the weak OTs of Figure \ref{SimpleProtCounter:ImplOA} (the full table is included in Appendix \ref{Appendix:FullExample}) :
+We can now show some of the weak OTs of Figure \ref{SimpleProtCounter:ImplWOA2} (the full table is included in Appendix \ref{Appendix:FullExample}) :
 \smallskip
@@
 {\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], ()}
-{S \OTWeakarrow {\texttt{p-a}} S}
-$ (for any state $S$)
+{s \OTWeakarrow {\texttt{p-a}} s}
+$ (for any  $s \in S$)
 
@@
          {\{\}, True, 
-   (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n, \texttt{s2\_ec}\gets \texttt{s1\_ec}+n)}
+   (\texttt{m1\_msg}\!\gets\! \texttt{s1\_msg}, \texttt{m1\_ec}\!\gets\! \texttt{s1\_ec}+n, \texttt{s2\_ec}\!\gets\! \texttt{s1\_ec}+n)}
          {100 \OTWeakarrow {\tau} 210}
@@
 
-$Post_{6a}=\ post_{4}\shortotimes\ Post_{456}^*\shortotimes\ post_{6}\\
-= \left( (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}, \texttt{s2\_ec}\gets \texttt{s1\_ec})
-\shortotimes (\texttt{s1\_ec}\gets \texttt{s1\_ec}+n) \right)
-\shortotimes (\texttt{s1\_ec}\gets \texttt{s2\_ec}+1) \\
-= (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets (\texttt{s2\_ec}+1)+n, \texttt{s2\_ec}\gets (\texttt{s2\_ec}+1)+n)$
+   \medskip     
+The  \Post~of of the weak OT $ WI_{6a}$ is:\\
+
+$
+\begin{array}{ll}
+Post_{6a}= post_{4}\shortotimes\ post_{456*}\shortotimes\ post_{6} =&  (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}, \texttt{s2\_ec}\gets \texttt{s1\_ec})\,
+\shortotimes \\ &(\texttt{s1\_ec}\gets \texttt{s1\_ec}+n) 
+\shortotimes (\texttt{s1\_ec}\gets \texttt{s2\_ec}+1) =\\
+&(\texttt{m1\_msg}\!\gets \texttt{s1\_msg}, \texttt{m1\_ec}\!\gets \texttt{s2\_ec}+1\!+\!n, \texttt{s2\_ec}\!\gets \texttt{s2\_ec}+1\!+\!n)
+\end{array}$\\
 
@@
          (\texttt{m1\_ec}\gets \texttt{s1\_ec}+1+n, \texttt{s2\_ec}\gets \texttt{s2\_ec}+1+n)}
-         {220 \OTWeakarrow {\tau} 210}
-         $($\forall n\ge 0$)
-
-$Post_{8c}= post_{8}\shortotimes\ post_{7}\shortotimes\ post_{4}\shortotimes\ Post_{456}^* 
+         {220 \OTWeakarrow {\tau} 210} \forall n\ge 0
+         $
+
+$Post_{8c}= post_{8}\shortotimes\ post_{7}\shortotimes\ post_{4}\shortotimes\ post_{456*} 
 = (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_msg}+1+n), \forall n\ge 0$
@@
          {\{\texttt{Q}\mapsto \texttt{q-recv(s1\_msg,s2\_ec}+n)\}, True, ()}
-         {210 \OTWeakarrow {\underline{\texttt{out(r1\_msg,r1\_ec)}\subst{(\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_msg}+n)}}} 202}
-        $($\forall n\ge 0$)
+         {210 \OTWeakarrow {\underline{\texttt{out(r1\_msg,r1\_ec)}\subst{(\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_msg}+n)}}} 202} \forall n\ge 0
+        $
 
@@
 \begin{definition}[Notation: Semantics of pNets as a weak open automaton]
-Let $A$ be the open automaton expressing the semantics of an open pNet $\pNet$; let $<J,\mathcal{S},s_0,  \WT>$ be the weak open automaton derived from $A$; this weak open automaton defines the weak semantics of the pNet $\pNet$.
+Let $A$ be the open automaton expressing the semantics of an open pNet $\pNet$; let $<J,\mathcal{S},s_0, V, \WT>$ be the weak open automaton derived from $A$; this weak open automaton defines the weak semantics of the pNet $\pNet$.
 Then, we denote $\pNet \models \WOT$ whenever $\WOT\in\WT$.

### 2020-04-17 2016-Weak-FH-Bisim/WeakBisim.tex
Resolved merge conflict by incorporating both suggestions.

@@
 
+\newcommand{\nounderline}[1]{#1}
+
 %\usepackage[math]{cellspace}
@@
          {\text{b1} \OTWeakarrow \tau \text{b1}} \forall n \geq 0$.
-Finally,  applying again \WTTrois, and using the central open transition having \texttt{\underline{out(b1\_m,b1\_ec)}}  as $\alpha$, we get the resulting weak open transition between b1 and b0 (as shown in Figure \ref{WOT2}).
+Finally,  applying again \WTTrois, and using the central open transition having \texttt{\nounderline{out(b1\_m,b1\_ec)}}  as $\alpha$, we get the resulting weak open transition between b1 and b0 (as shown in Figure \ref{WOT2}).
+
  %     $\openrule
@@
          {\{\texttt{Q}\mapsto \texttt{q-recv(s1\_msg,s2\_ec}+n)\}, True, ()}
-         {210 \OTWeakarrow {\underline{\texttt{out(r1\_msg,r1\_ec)}\subst{(\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_msg}+n)}}} 202} \forall n\ge 0
-        $
+        {210 \OTWeakarrow {\nounderline{\texttt{out(r1\_msg,r1\_ec)}\subst{(\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_msg}+n)}}} 202}
+        $($\forall n\ge 0$)
 
@@
         $
+
+\TODO{ajouter les boucles de $WI_1$ et $WI_2$, dans le cas ou $p_a$ (resp $q_b$) sont des $\tau$:}
+
+$WI_{12*}(n) = \openrule
+{\{(\texttt{P}\mapsto \tau|\texttt{Q}\mapsto \tau)^n\},true, ()}
+  {s \OTWeakarrow {\tau} s} 
+s \in S$
 

### 2020-04-17 2016-Weak-FH-Bisim/WeakBisim.tex
correct version

@@
         {\text{b1} \OTWeakarrow \tau \text{b1}} \forall n \geq 0$.
-Finally,  applying again \WTTrois, and using the central open transition having \texttt{\nounderline{out(b1\_m,b1\_ec)}}  as $\alpha$, we get the resulting weak open transition between b1 and b0 (as shown in Figure \ref{WOT2}).
+Finally,  applying again \WTTrois, and using the central open transition having \texttt{\nounderline{out(out(b1\_m,b1\_ec)}}  as $\alpha$, we get the resulting weak open transition between b1 and b0 (as shown in Figure \ref{WOT2}).
 
@@
 
+\medskip
 $Post_{8c}= post_{8}\shortotimes\ post_{7}\shortotimes\ post_{4}\shortotimes\ post_{456*} 
@@
 
+ \medskip  
 $ WI_{8c}(n) = \openrule
          {\{\texttt{Q}\mapsto \texttt{q-recv(s1\_msg,s2\_ec}+n)\}, True, ()}
-        {210 \OTWeakarrow {\nounderline{\texttt{out(r1\_msg,r1\_ec)}\subst{(\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_msg}+n)}}} 202}
-        $($\forall n\ge 0$)
+         {210 \OTWeakarrow {\nounderline{\texttt{out(r1\_msg,r1\_ec)}\subst{(\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_msg}+n)}}} 202}\forall n\ge 0
+        $
 

### 2020-04-17 2016-Weak-FH-Bisim/WeakBisim.tex
changes over skype

@@
 we define the composition operation as follows: 
-\TODO{version d eric reprise et corrigee}
+%\TODO{version d eric reprise et corrigee}
 %$(x_k\gets e_k)^{k\in K}\shortotimes \Post =  (x_k\gets e_k\subst{\Post})^{k\in K}$
@@
 
-$(x_{k}\gets e_{k})^{k\in K}\shortotimes (x'_{k'}\gets e'_{k'})^{k'\in K'} =  
-(x_{k}\gets e_{k}\subst{(x'_{k'}\gets e'_{k'})^{k'\in K'}})^{k\in K} \cup (x'_{k'}\gets e'_{k'})^{k'\in K''}$\\
+\[(x_{k}\gets e_{k})^{k\in K}\shortotimes (x'_{k'}\gets e'_{k'})^{k'\in K'} =  
+(x_{k}\gets e_{k}\subst{(x'_{k'}\gets e'_{k'})^{k'\in K'}})^{k\in K} \cup (x'_{k'}\gets e'_{k'})^{k'\in K''}\]
 where $K''=\{k'\in K'|x'_{k'}\not\in\{x_k\}^{k\in K}\}$
@@
 A pLTS is a tuple
-$\pLTS\triangleq\mylangle S,s_0, \to\myrangle$ where:
+$\pLTS\triangleq\mylangle S,s_0, V, \to\myrangle$ where:
 \begin{itemize}
@@
 %by the additional assignments.
+\item[$\bullet$] $V$ is a set of global variables for the pLTS,
 \item[$\bullet$] $\to \subseteq S \times L \times S$ is the transition relation and 
@@
 % REMOVED BECAUSE USELESS: $\iv(\alpha)\!\subseteq\! \vars(s')$, 
-		$\vars(\alpha)\backslash \iv(\alpha)\!\subseteq\! \vars(s)$, 
+		$\vars(\alpha)\backslash \iv(\alpha)\!\subseteq\! V$, 
 		$\vars(e_b)\!\subseteq\! \vars(s)\cup\vars(\alpha)$, and
-		$\forall j\!\in\! J .\,\left(\vars(e_j)\!\subseteq\! \vars(s)\cup\vars(\alpha)\land 
-		x_j\!\in\!\vars(s') \right)$. %,  and $s= s'\Rightarrow J=\emptyset$.
-\hl{Additionally we require that:} $\{x_j|j\in J\} = \vars(s')$.
+		$\forall j\!\in\! J .\,\left(\vars(e_j)\!\subseteq\! V\cup\vars(\alpha)\land 
+		x_j\!\in V \right)$. %,  and $s= s'\Rightarrow J=\emptyset$.
+
 %\LUDO{I suggest to add: $\{x_j|j\in J\} = \vars(s')$ or $\{x_j|j\in J\} \cup \iv(\alpha)= \vars(s')$} 
@@
   \symb{SV}_k\!=\!\SV{\alpha_{l}^{l\in I_k \uplus J_k}}{\alpha'_k}{e_k}$ \hl{where}
-  $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
+  $\alpha'_k\in \AlgAS$, $I_k\subseteq I$, $J_k\subseteq J$,
   $\forall i\!\in\!
@@
   \begin{itemize}
-  \item The sort of a pNet is its signature, i.e. the set of actions it can
+  \item The sort of a pNet is its signature, i.e. the set of actions in $\AlgAS$ it can
 perform, where each action signature is an action 
@@
 \begin{array}{l}
-\Sortop(\mylangle S,s_0, \to\myrangle) = \{\alpha\subst{?x \gets x| 
+\Sortop(\mylangle S,s_0,V, \to\myrangle) = \{\alpha\subst{?x \gets x| 
 x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
@@
 
-\item The set of variables of a pNet $P$, denoted $vars(P)$ is the set of variables of all states of all pLTSs that compose $P$.
+\item The set of variables of a pNet $P$, denoted $vars(P)$ is the set of variables of  all pLTSs that compose $P$.
 
@@
   \[\begin{array}{l}
-\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset\\
+\Holes(\mylangle S,s_0,V, \to\myrangle) \!=\! \emptyset\\
 \Holes(\mylangle \pNet_i^{i\in I}\!,\set{\Sort}, \set{\symb{SV}}\myrangle) 
@@
 \[\begin{array}{l}
-\Leaves(\mylangle S,s_0, \to\myrangle) \!=\!\emptyset\\%\{\mylangle S,s_0, \to\myrangle\}\\
+\Leaves(\mylangle S,s_0,V, \to\myrangle) \!=\!\emptyset\\%\{\mylangle S,s_0, \to\myrangle\}\\
 \Leaves(\mylangle \pNet_i^{i\in I}\!,%Sort_j^{j\in J}
@@
 \subsection{Open Automata}
- Open automata (OA) are not composition structures but they are made of transitions that are dependent of the actions of the holes, and they can reason on variables (potentially with only symbolic values).
-Formaly, each state of an OA has a set of \emph{state variables}, and all state variable sets are disjoint.
+ Open automata (OA) are not composition structures but they are made of transitions that are dependent of the actions of the holes, and they can reason on a set of variables (potentially with only symbolic values).
 %\TODO{adopt a uniform notation for open transitions, almost each instance has a 
@@
 	An \emph{open transition} (OT) over a
-	set $J$ of holes with sorts $\Sort_j^{j\in J}$ and a set of states $\mathcal{S}$ is 
+	set $J$ of holes with sorts $\Sort_j^{j\in J}$, a set V of variables, and a set of states $\mathcal{S}$ is 
 	a structure of the form:	
@@
         label denoting the resulting action of this open transition.
-        We call \emph{source variables} of an OT the union of all variables
+%        We call \emph{source variables} of an OT the union of all variables
+%        in the different terms
+%        $\beta_j$ and $\alpha$, and the state variables of $s$.
+        \Pred\ is a predicate over the  variables $V$ and all variables
         in the different terms
-        $\beta_j$ and $\alpha$, and the state variables of $s$.
-        \Pred\ is a predicate over the source variables. \Post\ is a set of 
+       $\beta_j$ and $\alpha$. \Post\ is a set of 
 	assignments that are effective \emph{after the open transition}, they are
         represented as a substitution of the form $({x_k\gets e_k})^{k\in K}$ 
-	where $x_k$ are\ \ERIC{the state variables of $s'$}\footnote{all of them, completed by identity if needed}, and $e_k$ are expressions
-        over the \ERIC{source or target state variables}\footnote{On pourrait du coup y mettre ici n'importe quelle variable du OA...}. Open transitions are identified
+	where $\forall k.\, x_k\in V$, and $e_k$ are expressions
+        over the variables $V$ and all variables
+        in the different terms
+       $\beta_j$ and $\alpha$. Open transitions are identified
         modulo logical equivalence on their predicate. 
@@
 inference rule. They correspond to two different logical levels.
- The open transition is itself a logical implication, but using a simple logic (this logic includes the boolean expressions $\AlgB$, boolean operators, and term equality).
-\hl{We differentiate classical (black) inference rules that use  an expressive logic and are paper rules from open transition rules that use a simpler  logic,  will be embedded into automata transitions, and could typically be handled in a
- mechanical way.}
+On one side, classical (black) inference rules  use  an expressive logic and are paper rules.
+ On the other side, open transition rules (with dotted lines) are logical implications, but using a simple logic (this logic includes the boolean expressions $\AlgB$, boolean operators, and term equality).
+   open transitions could typically be handled in a 
+ mechanised way.
 
@@
 an expression. More formally, let $\Post$ be any substitution and
-$\Pred$ any predicate; suppose $\vars(t)\cap \dom(\Post)=\emptyset$ and
-$\vars(t')\cap \dom(\Post)=\emptyset$. Then we have the following
+$\Pred$ any predicate; suppose $V\cap \dom(\Post)=\emptyset$. Then we have the following
 implication:
@@
 
-\subsubsection*{Note on finite versus infinite open automata:} as
-mentionned in page \pageref{def:open-automaton}, we have defined two flavors of
-automata. More precisely, in \cite{hou:hal-02406098}, we formely define
+\subsubsection*{Note on finite versus infinite open automata:} 
+As mentioned in Definition \pageref{def:open-automaton}, we adopt here a semantic view on open automata. More precisely, in \cite{hou:hal-02406098}, we formely define
 \emph{semantic open automata} (infinite as in Definition \ref{def:open-automaton}),
@@
 the predicates inclusion is decidable over  
-\hl{the action algebra} $\mathcal{A}_P$. Then it is decidable whether the relation 
+the action algebra $\AlgA$. Then it is decidable whether the relation 
 $\mathcal{R}$ is a FH-bisimulation.
@@
 
-  For any pNet \pNet, let $\Leaves(\pNet) = \mylangle S_i,{s_i}_0, \to_i\myrangle^{i \in L}$ be 
+  For any pNet \pNet, let $\Leaves(\pNet) = \mylangle S_i,{s_i}_0,V, \to_i\myrangle^{i \in L}$ be 
   the set of pLTS at its leaves,
@@
 A pLTS being its own single leave:
-  $States(\mylangle S,s_0, \to\myrangle) = \{\triangleleft s \triangleright| s \in S, \}$.
+  $States(\mylangle S,s_0,V, \to\myrangle) = \{\triangleleft s \triangleright| s \in S, \}$.
 To be precise, the state of a pLTS is not reduced to a state identity, it also contains the value of its variables $vars(P)$.
@@
 \begin{definition}[Semantics of open pNets]
-	\label{def:operationalSemantics}
-\hl{The semantics of a pNet} $\pNet$ is an open automaton $A\!= 
+	\label{def:operationalSemantics} The semantics of a pNet $\pNet$ is an open automaton $A\!= 
 	<\!\!Holes(\pNet),States(\pNet),InitState(\pNet),vars(P),\mathcal{T}\!\!>$ where $\mathcal{T}$   is the smallest set of open transitions such that $\mathcal{T}=\{OT\,|\,\pNet \models OT \}$ and	$\pNet \models OT$	is defined by the following  rules:
@@
 
-\paragraph{Example} \hl{Figure} \ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the Specification pNet given in Figure \ref{SimpleProt:Spec}. 
+\paragraph{Example} \hl{paragraph} Figure~\ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the Specification pNet given in Figure \ref{SimpleProt:Spec}. 
 For later references, we give to the transitions of this (strong)

### 2020-04-20 2016-Weak-FH-Bisim/WeakBisim.tex
highligts fixed

@@
 A pNet has a set of sub-pNets that can be either pNets or pLTSs, and a
-set of Holes, playing the role of process parameters. A pNet is thus a composition operator that can receive processes as parameters; it expresses how the actions of the sub-processes synchronise.
+set of holes, playing the role of process parameters. A pNet is thus a composition operator that can receive processes as parameters; it expresses how the actions of the sub-processes synchronise.
 
@@
   synchronisation vectors. $\forall k\!\in\! K,
-  \symb{SV}_k\!=\!\SV{\alpha_{l}^{l\in I_k \uplus J_k}}{\alpha'_k}{e_k}$ \hl{where}
+  \symb{SV}_k\!=\!\SV{\alpha_{l}^{l\in I_k \uplus J_k}}{\alpha'_k}{e_k}$ where
   $\alpha'_k\in \AlgAS$, $I_k\subseteq I$, $J_k\subseteq J$,
@@
 It acts as the parallel operator.
-It consists of three nodes: two Holes $P$ and $Q$ and one subnet, denoted {\it PrefectBuffer}.
+It consists of three nodes: two holes $P$ and $Q$ and one subnet, denoted {\it PrefectBuffer}.
 Nodes of the tree are synchronized using four synchronization vectors, that  express the possible synchronizations between the parameterized actions of a subset of the nodes.
@@
 The equivalence we need is a strong bisimulation between
-pNets having exactly the same Holes with the same sorts, but using a
+pNets having exactly the same holes with the same sorts, but using a
 flexible matching 
@@
     \smallskip
-    The global states here are triples, build as the product of states of the 3 pLTS (remember the Holes have no state). The assignment
+    The global states here are triples, build as the product of states of the 3 pLTS (remember the holes have no state). The assignment
     $Post$ uses the variable $\texttt{m}$ from the action of hole $\texttt{P}$ to set the
@@
 	include one {\em open transition} for each sub-pNet involved, one possible
-	{\em action} for each Hole involved, and the predicate relating these
+	{\em action} for each hole involved, and the predicate relating these
 	with the resulting action of the vector. The sub-pNets involved are split between two 
@@
 
-\paragraph{Example} \hl{paragraph} Figure~\ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the Specification pNet given in Figure \ref{SimpleProt:Spec}. 
+\subsection*{Example}  Figure~\ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the Specification pNet given in Figure \ref{SimpleProt:Spec}. 
 For later references, we give to the transitions of this (strong)

### 2020-04-21 2016-Weak-FH-Bisim/WeakBisim.tex
passe sur le corps du papier

@@
 used inside states, actions, guards, and
-assignments. Without loss of generality and to simplify the formalisation, we suppose 
- that variables are local to each 
-state: each state has its set of variables disjoint from the ones of the other states. Transmitting the value of
-variables from one state to another can be done by explicit assignment. 
+assignments. 
 %Similarly, to simplify the management of variables and without loss of expressivity, we 
@@
 
+The semantics of the assignments is that a set of assignments between two states is performed in parallel so that their order do not matter and they all use the values of variables before the transition (or the values received as action parameters).
+
 Now we define
@@
 of holes, leaves and sorts formalised below in Definition~\ref{def-sortholeleave}.
-Informally, holes are process parameters, leavs provide the set of pLTSs at the leaves of the hierarchical structure of a pNet, and sorts give the signature of a pNete, i.e.
+Informally, holes are process parameters, leaves provide the set of pLTSs at the leaves of the hierarchical structure of a pNet, and sorts give the signature of a pNete, i.e.
 the actions it exposes.
@@
 The return $\symb{ack}$ message from $\symb{Receiver}$ to $\symb{Sender}$ is supposed to be safe.
-The final transmission of the message to the recipient (the hole Q) includes the value of the ``error counter'' $ec$.
+The final transmission of the message to the recipient (the hole $Q$) includes the value of the ``error counter'' $ec$.
 
 Fig. \ref{SimpleProt:Spec} (right) shows a graphical view of the pNet that specifies the system:
-the full system should be equivalent (e.g. through weak bisimulation)
+the full system should be equivalent (e.g.  weakly bisimilar)
 to the two processes connected simply through a perfect medium.  
@@
 For instance, in the vector "$< \texttt{p-send(m)},\texttt{in(m)},\_> \rightarrow \texttt{\nounderline{in(m)}}$" only $P$ and {\it PrefectBuffer} nodes are involved in the synchronization.
-The synchronization between these processes occurs when  process $P$  performs $\texttt{p-send(m)}$  action sending a message, and  the {\it PrefectBuffer} accepts the message through $\texttt{in(m)}$ action  at the same time; the result that will be returned at upper level is the action  $\texttt{\nounderline{in(m)}}$.
+The synchronization between these processes occurs when  process $P$  performs $\texttt{p-send(m)}$  action sending a message, and  the {\it PrefectBuffer} accepts the message through an $\texttt{in(m)}$ action  at the same time; the result that will be returned at upper level is the action  $\texttt{\nounderline{in(m)}}$.
 
@@
 \ref{SimpleProt:Impl} shows the pNet model of the protocol implementation.
-When the $\symb{Medium}$ detects an error (modeled by a local $\tau$ action), it sends back a $\texttt{m\_error}$ message to the $\symb{Sender}$.
+When the $\symb{Medium}$ detects an error (modelled by a local $\tau$ action), it sends back a $\texttt{m\_error}$ message to the $\symb{Sender}$.
 The $\symb{Sender}$ increments its local error counter $ec$, and resends the message (including $ec$) to the $\symb{Medium}$, that will, eventually, transmit $m,ec$ to the $\symb{Receiver}$.
@@
 	An \emph{open transition} (OT) over a
-	set $J$ of holes with sorts $\Sort_j^{j\in J}$, a set V of variables, and a set of states $\mathcal{S}$ is 
+	set $J$ of holes with sorts $\Sort_j^{j\in J}$, a set $V$ of variables, and a set of states $\mathcal{S}$ is 
 	a structure of the form:	
@@
         in the different terms
-       $\beta_j$ and $\alpha$. Open transitions are identified
+       $\beta_j$ and $\alpha$. Because the variables in $V$ can be in both side of the assignments, the assignments are always applied in a parallel manner. Open transitions are identified
         modulo logical equivalence on their predicate. 
@@
 
-An open automaton is then simply an automaton where each transition is an open transition.
+An open automaton is  an automaton where each transition is an open transition.
 \begin{definition}[Open automaton]
@@
 The equivalence we need is a strong bisimulation between
-pNets having exactly the same holes with the same sorts, but using a
+open automata having exactly the same holes with the same sorts, but using a
 flexible matching 
-between open transitions, to accommodate comparisons between pNet
-expressions with different architectures.
+between open transitions, this will allow us to compare pNets
+with different architectures.
 
@@
  Then 
-$\mathcal{R}$ is an FH-bisimulation iff for any  states
+$\mathcal{R}$ is an FH-bisimulation if and only if for any  states
 $s\in\mathcal{S}_1$ and $t\in\mathcal{S}_2$, $(s,t|\Pred_{s,t})\in\mathcal{R}$, we 
@@
 \end{mathpar}
- such that  $\forall x, J'=J_{x}, \exists \Pred_{s',t_x}. (s',t_x|\Pred_{s',t_x})\in 
- \mathcal{R}$; 
+ such that  $\forall x, J'=J_{x}$ and there exists $\Pred_{s',t_x}$ such that $(s',t_x|\Pred_{s',t_x})\in 
+ \mathcal{R}$
  and  \\
@@
   $States(\mylangle S,s_0,V, \to\myrangle) = \{\triangleleft s \triangleright| s \in S, \}$.  
-To be precise, the state of a pLTS is not reduced to a state identity, it also contains the value of its variables $vars(P)$.
 %This could be encoded as a mapping from variables of the pNet to expressions, of the form: $\sigma=\{x_i\to e_i\}^{i\in I},\,(x_i\in vars(S))$.
@@
 \end{definition}
+To be precise, the state of each pLTS is entirely characterised by both the state of the automaton, and the value of its variables $V$.
+Consequently, the complete characterization of the state of a pNet should take into account the value of its variables $vars(P)$.
 
@@
 
-\TODO{Check, nouvelle formulation, Eric}
-\LUDO{checked, slight changes}
 Thus, we let $\gamma$ range over sequences of action terms and use $\dotcup$ as the concatenation operator that appends sequences of action terms: given two sequences of action terms  $\gamma\dotcup\gamma '$ concatenates the two sequences.
@@
 
+\LUDO{il faudrait mieux introduire le paragraphe ci dessous pour expliquer ce qu'il fait ici}
 In practice, we are dealing with finite representations of the (infinite) open automata.
@@
 \end{theorem}
-The proof  is detailed in Appendix \ref{app-WFH-equiv}, it follows a similar pattern as the proof that strong FH-bisimulation is an equivalence, but technical details are different, and in practice we rely on a different (but proven equivalent) definition of weak FH-bisimilarity; this equivalent version simulates a \emph{weak} open transition with a set of weak open transition.
+The proof  is detailed in Appendix \ref{app-WFH-equiv}, it follows a similar pattern as the proof that strong FH-bisimulation is an equivalence, but technical details are different, and in practice we rely on a variant of the definition of weak FH-bisimilarity; this equivalent version simulates a \emph{weak} open transition with a set of weak open transition.
 The careful use of the best definition of weak FH-bisimilarity makes the proof similar to the strong FH-bisimulation case.
@@
 
-When silent actions cannot be observed, weak bisimulation is a congruence for open pNets: if $P$ and $Q$ are weakly bisimilar to $P'$ and $Q'$ then the composition of $P$ and $Q$ is weakly bisimilar to the composition of$P'$ and $Q'$, where composition is the hole replacement operator: 	$\pNet[\pNetQ]_{j}$ and
+When silent actions cannot be observed, weak bisimulation is a congruence for open pNets: if $P$ and $Q$ are weakly bisimilar to $P'$ and $Q'$ then the composition of $P$ and $Q$ is weakly bisimilar to the composition of $P'$ and $Q'$, where composition is the hole replacement operator: 	$\pNet[\pNetQ]_{j}$ and
 	$\pNet'[\pNetQ']_{j}$ are weak FH-bisimilar. This can be shown by proving the two following theorems.
@@
 	ensured by 
-	strong bisimilarity.}. Then 
+	weak bisimilarity.}. Then 
 	$\pNet[\pNetQ]_{j_0}$ and 

### 2020-04-21 2016-Weak-FH-Bisim/WeakBisim.tex
sectionning in the appendix

@@
 \appendix    
-
-       \section{Bisimulation is an equivalence: Proof of Theorem~\ref{thm-equiv}}\label{thm-equiv-proof}
+\section{Proof on FH-bisimulation}
+\subsection{Bisimulation is an equivalence: Proof of Theorem~\ref{thm-equiv}}\label{thm-equiv-proof}~\\
         \emph{Suppose $\mathcal{R}$ 
@@
 
-       \section{Proofs of properties on pNets}
 \subsection{Composition Lemmas}       
-       The proof of the other theorems rely on two main lemmas,
+       The proofs of the composition theorems for FH-bisimulation rely on two main lemmas,
 dealing respectively with the decomposition of a composed behaviour
@@
 
-\paragraph{Lemma~\ref{lem-decompose}}: {\bf Open transition decomposition} \\
+\subsubsection*{{\bf Lemma~\ref{lem-decompose}}: Open transition decomposition} ~\\
  Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$}.
@@
 
-\paragraph{\bf Lemma~\ref{lem-compose}} {\it Open transition composition}\\
-	Suppose $j_0\in J$ and:\\[-2ex]
+\subsubsection*{ \bf{Lemma~\ref{lem-compose}}:  Open transition composition}~\\
+	Suppose $j_0\in J$ and:\\[-1ex]
 \begin{mathpar}
@@
 \end{mathpar}
-Then, we have\\[-2ex]
+Then, we have\\[-1ex]
 	\[ P[Q]_{j_0}  

### 2020-04-21 2016-Weak-FH-Bisim/WeakBisim.tex
corrected erroneous todos for tau transitions of holes
and added a summary table in last Appendix.

@@
 Remark that in our simple example no $\tau$ transition involves any visible action from a hole, so we have no $\beta$ sequences of length longer than 1 in the weak automaton.
-\TODO{en fait c'est faux ! les boucles SS\_1, SS\_2, WS\_1, WS\_2 sont aussi valides avec p\_a ou q\_b = tau, donc on peut avoir des sequences de longueur arbitraire d'actions de P et de Q}
+%\TODO{en fait c'est faux ! les boucles SS\_1, SS\_2, WS\_1, WS\_2 sont aussi valides avec p\_a ou q\_b = tau, donc on peut avoir des sequences de longueur arbitraire d'actions de P et de Q}
 
@@
         {\text{b1} \OTWeakarrow \tau \text{b1}} \forall n \geq 0$.
-Finally,  applying again \WTTrois, and using the central open transition having \texttt{\nounderline{out(out(b1\_m,b1\_ec)}}  as $\alpha$, we get the resulting weak open transition between b1 and b0 (as shown in Figure \ref{WOT2}).
+Finally,  applying again \WTTrois, and using the central open transition having \texttt{\nounderline{out(b1\_m,b1\_ec)}}  as $\alpha$, we get the resulting weak open transition between b1 and b0 (as shown in Figure \ref{WOT2}).
 
@@
 
-\TODO{ajouter les boucles de $WI_1$ et $WI_2$, dans le cas ou $p_a$ (resp $q_b$) sont des $\tau$:}
-
-$WI_{12*}(n) = \openrule
-{\{(\texttt{P}\mapsto \tau|\texttt{Q}\mapsto \tau)^n\},true, ()}
-  {s \OTWeakarrow {\tau} s} 
-s \in S$
+%\TODO{ajouter les boucles de $WI_1$ et $WI_2$, dans le cas ou $p_a$ (resp $q_b$) sont des $\tau$:}
+%
+%$WI_{12*}(n) = \openrule
+%{\{(\texttt{P}\mapsto \tau|\texttt{Q}\mapsto \tau)^n\},true, ()}
+%  {s \OTWeakarrow {\tau} s} 
+%s \in S$
+
+\bigskip
+The following table give a summary of  WOTs, when sharing their names as much as possible.
+
+\begin{tabular}{|l|l|c|}
+\hline
+    WOT name & Pairs of source states and target states & \# of WOTs \\
+    \hline
+    $WI_1$ $WI_2$ $WI_\tau$ & $\{(s,s)| s \in \texttt{States of WOA}\} \cup \{(202,000)\} $ & 21 \\
+    $WI_3(n)$ & \{(202,100),(000,100)\} & 2 \\
+    $WI_{3a}(n)$ & \{(202,210),(000,210)\} & 2 \\
+    $WI_{3b}(n)$ & \{(202,220),(000,220)\} & 2 \\
+    $WI_{3c}(n)$ & \{(202,201),(000,201)\} & 2 \\
+    $WI_4(n)$ $WI_4P(n)$ $WI_4Q(n)$ & \{(100,210)\} & 3 \\
+    $WI_{4a}(n)$ $WI_4aP(n)$ $WI_4aQ(n)$ & \{(100,220)\} & 3 \\
+    $WI_{456*}(n) $ $WI_{456*}P(n) $ $WI_{456*}Q(n) $ & \{(100,100)\} & 3 \\
+    $WI_5(n)$ $WI_5P(n)$ $WI_5Q(n)$ & \{(210,220)\} & 3 \\
+    $WI_{5a}(n)$ $WI_{5a}P(n)$ $WI_{5a}Q(n)$ & \{(210,100)\} & 3 \\
+    $WI_{564*}(n) $ $WI_{564*}P(n) $ $WI_{564*}Q(n) $ & \{(210,210)\} & 3 \\
+    $WI_6(n)$ $WI_6P(n)$ $WI_6Q(n)$ & \{(220,100)\} & 3 \\
+    $WI_{6a}(n)$ $WI_{6a}P(n)$ $WI_{6a}Q(n)$ & \{(220,210)\} & 3 \\
+    $WI_{645*}(n) $ $WI_{645*}P(n) $ $WI_{645*}Q(n) $ & \{(220,220)\} & 3 \\
+    $WI_7(n)$ $WI_7P(n)$ $WI_7Q(n)$ & \{(210,201)\} & 3 \\
+    $WI_{7a}(n)$ $WI_{7a}P(n)$ $WI_{7a}Q(n)$ & \{(220,201)\} & 3 \\
+    $WI_{7b}(n)$ $WI_{7b}P(n)P$ $WI_{7b}Q(n)$ & \{(100,201)\} & 3 \\
+    $WI_8(n)$ & \{(201,202),(201,000)\} & 2\\ 
+    $WI_{8a}(n)$ & \{(210,202),(210,000)\} & 2 \\
+    $WI_{8b}(n)$ & \{(220,202),(220,000)\} & 2 \\
+    $WI_{8c}(n)$ & \{(100,202),(100,000)\} & 2 \\
+
+    \hline
+    \end{tabular}
+    \bigskip
+    That makes a total of 73 WOTs  in the SimpleImpl WOA.
 
@@
 
-         And these numbers raise faster for other states, e.g. 13 WOTs for state 100.
+       Full list of WOTs
 

### 2020-04-21 2016-Weak-FH-Bisim/WeakBisim.tex
lecture part 1

@@
        	\[\mathcal{R}'' = 
-       	\{(s,u|\Pred_{s,u})\,\,\Big|\,\Pred_{s,u}=\bigvee_{\begin{array}{c}       		
+       	\{(s,u|\Pred_{s,u})\,\,\Big|\,\Pred_{s,u}=\hspace{-0.7cm}\bigvee_{\begin{array}{c}       		
        		(s,t|\Pred_{s,t})\in\mathcal{R}\\ (t,u|\Pred_{t,u})\in\mathcal{R}' 	
        		\end{array}
-       	}\,\Pred_{s,t}\land\Pred_{t,u}\}\]
+       }\hspace{-0.5cm}\Pred_{s,t}\land\Pred_{t,u}\}\]
 
@@
        	More precisely,  $t_{px} \in ({t'_p})^{p\in P'}$ where $({t'_p})^{p\in 
-       		P'}$ is 
+       		P'}$\hl{$P'\subseteq P$} is 
        	the set of states relating ${s}'$ and $u_{pxy}$ (the states used in the open transition must belong to the set of states ensuring the transitive relation).
@@
 we can suppose that, as $\Pred\,'_{{pxy}}$ is used to relate states of 
-$\mathcal{T}_1$, and $\mathcal{T}_3$, there exists a predicate obtained by 
+$\mathcal{T}_1$ and $\mathcal{T}_3$, there exists a predicate obtained by 
 renaming variables, that is equivalent to $\Pred\,'_{{pxy}}$ and does not 
-contain the variables of 	$\mathcal{T}_2$. This predicate with ``fresh'' 
-variables is called   $\Pred\,'_{{pxy}}$ in the following.
+contain the variables of 	$\mathcal{T}_2$. This \hl{predicate with ``fresh'' 
+variables is called}   $\Pred\,'_{{pxy}}$ in the following.
 Similarly, we can suppose that $\Pred_{{px}}$ contains no 
@@
        	\end{small}
+
 From (*) and (**) we have, for all $p$
@@
        		\big( \forall j'. \beta_{j'px}=\beta_{j'pxy}  \land \Pred_{OT_{pxy}}
-       		\land \alpha_{px}\!=\!\alpha_{pxy}\\~\hspace{3em}~ \land
+       		\land \alpha_{px}\!=\!\alpha_{pxy}\\~\hspace*{2em}~ \land
        		\Pred_{{pxy}}\subst{\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}\big))
@@
        		\Pred_{OT_{pxy}}
-       		\land \alpha\!=\alpha_{px}\!=\!\alpha_{pxy}\\~\hspace{3.5em}~ \land
+       		\land \alpha\!=\alpha_{px}\!=\!\alpha_{pxy}\\~\hspace*{2em}~ \land
        		\Pred_{{pxy}}\subst{\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}
@@
 variables of the open automaton they belong to. Finally, because of the domain of the 
-substitutions  and of the predicates, we have:\\
+substitutions of the predicates, we have:\\
        	$\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\land 
-       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}\\
-       	\Leftrightarrow % we changed =
+       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}\uplus
+       	\Post_{OT_{pxy}}}\Leftrightarrow\\ % we changed =
        	\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}\land
        	\Pred_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}\\
-       	\implies\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}\\
-       	\Leftrightarrow % we changed = 
+       	\implies\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus
+       	\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}
+       	\Leftrightarrow\\ % we changed = 
        	 \Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{pxy}}} $\\
@@
 \big( \forall j, j'.\beta_j=\beta_{jpx} \land \beta_{j'px}=\beta_{j'pxy}
-\land\\ ~\hspace{7em} 
-\Pred_{OT_{pxy}}
-\land \alpha\!=\!\alpha_{px}\!=\!\alpha_{pxy}\land\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus \Post_{OT_{pxy}}}\big)
+\land \Pred_{OT_{pxy}}\\
+~\hspace*{2em}~\land \alpha\!=\!\alpha_{px}\!=\!\alpha_{pxy}\land\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus \Post_{OT_{pxy}}}\big)
 \\
@@
 		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.
-		 Then there exist $\alpha_Q$, $\Pred\,'$, $\Pred\,''$, 
+		 Then, there exist $\alpha_Q$, $\Pred\,'$, $\Pred\,''$, 
 		$\Post\,'$, $\Post\,''$ s.t.:\\[-2ex]
@@
 \\     	
-	\forall m\!\!\in\!\! I_1. {\pNet_m 
+	\forall m\!\in\! I_1. {\pNet_m 
 	\models\openrule
@@
   \qquad
-\forall m\!\!\in\!\! I_2.		{ \pNet_m 
+\forall m\!\in\! I_2.		{ \pNet_m 
     	 \models
@@
 
-Now focus on OTs\footnote{In the appendix we use OT to abbreviate ``open transition'' and WOT to stand for ``weak open transition.''} of the subnets.
+\hl{Now focus on OTs}\footnote{In the appendix we use OT to abbreviate ``open transition'' and WOT to stand for ``weak open transition.''} of the subnets.
 For each $m\in I_1\uplus I_2$ we have one of the two
 following OT\footnotemark[\thefootnote]:\\
-for $m$ in $I_1$
+either $m$ in $I_1$
 \[
@@
     		\ostate{(s_i^\prime)^{i\in L_m}}}\]
-Or, $m$ in $I_2$
+or, $m$ in $I_2$
 \[{ \pNet_m 
@@
 
-Only elements of $(I_1\uplus I_2)\backslash\{j_0\}$ and  are useful to assert the premise for reduction of $P$; the last 
+\hl{Only elements of} $(I_1\uplus I_2)\backslash\{j_0\}$ and  are useful to assert the premise for reduction of $P$; the last 
 one ensures the open transition for the pNet $Q$ (note that $Q$ is at place $j_0$, and by 
@@
 	}\]
+\TODO{j'ai du mal, je reviens}
 
@@
 \qed
+
 \footnotetext{Cloning and freshness introduce alpha-conversion at many points 
@@
 \[
-    	\forall m\!\!\in\!\! I_1\uplus\{j_0\}. {\pNet_m 
+    	\forall m\!\in\! I_1\uplus\{j_0\}. {\pNet_m 
     	\models\openrule
@@
   \]\[
-\forall m\!\!\in\!\! I_2.		{ \pNet_m 
+\forall m\!\in\! I_2.		{ \pNet_m 
     	 \models

### 2020-04-22 2016-Weak-FH-Bisim/WeakBisim.tex
title sec
erasing of TODO

@@
 To illustrate this work, we use a simple communication protocol, that provides safe transport of data between two processes, over unsafe media.
-
-\TODO{J'ai change les $\underline{in}$ et $\underline{out}$ en $in$ et $out$ dans le texte. Rabea, peux-tu le faire dans toutes les figures (1, 2, 3,4,5,6) ?}
 
@@
 
-\subsection{Bisimulation for open pNets -- a Composable Bisimulation Theory}
+\subsection{Bisimulation for open pNets -- a composable bisimulation theory}
 \label{section:bisimulation-PN}
@@
 an operator that takes a set of actions performed by one hole and produces a sequence of observable actions.
-\TODO{Ca serai tpas mal de trouver une notation plus intuitive au lieu de ce $\vis{\set\beta}$ ?}
+
 Thus we define $\vis{\set\beta}$ as the mapping $\set\beta$  with only observable actions of the holes in $I$, but where each element is either empty or a list of length 1:
@@
 \begin{figure}[ht]
-   \centerline{\includegraphics[width=12cm]{XFIG/WOT2-result}}
+   \centerline{\includegraphics[width=13cm]{XFIG/WOT2-result}}
   \caption{Construction of an example of weak open transition}

### 2020-04-23 2016-Weak-FH-Bisim/WeakBisim.tex
A pass on lemma 1

@@
        	More precisely,  $t_{px} \in ({t'_p})^{p\in P'}$ where $({t'_p})^{p\in 
-       		P'}$\hl{$P'\subseteq P$} is 
+       		P'}$\hl{$P'\subseteq P$} \TODO{NO : there is no relation between the two sets: they are not comparable} is 
        	the set of states relating ${s}'$ and $u_{pxy}$ (the states used in the open transition must belong to the set of states ensuring the transitive relation).
@@
 name clash. In practice,
-we can suppose that, as $\Pred\,'_{{pxy}}$ is used to relate states of 
-$\mathcal{T}_1$ and $\mathcal{T}_3$, there exists a predicate obtained by 
-renaming variables, that is equivalent to $\Pred\,'_{{pxy}}$ and does not 
-contain the variables of 	$\mathcal{T}_2$. This \hl{predicate with ``fresh'' 
-variables is called}   $\Pred\,'_{{pxy}}$ in the following.
+we can suppose that $\Pred\,'_{{pxy}}$ does not 
+contain the variables of $\mathcal{T}_2$ because it is used to relate states of $\mathcal{T}_1$ and $\mathcal{T}_3$ .
+Indeed if $\Pred\,'_{{pxy}}$ uses variables of 	$\mathcal{T}_2$, we can consider instead another predicate that is equivalent to $\Pred\,'_{{pxy}}$ and does not
+contain the variables of 	$\mathcal{T}_2$ (this is safe according to the semantic interpretation of open automata and relations). 
 Similarly, we can suppose that $\Pred_{{px}}$ contains no 
@@
 
+\textbf{Preliminary note:}
+The introduction of fresh variables introduce alpha-conversion at many points 
+of the proof; we 
+	only 
+	give major arguments concerning alpha-conversion to make the proof readable; in 
+	general, fresh variables appear in each transition inside
+        terms $\beta_j$, $v$, and 
+	$\Pred$.
+
    \begin{proof}
+
 Consider rule \TrDeux\ in 
@@
 
-First, $K$ and the synchronisation vector $SV_k$ are unchanged\footnotemark (however 
+First, $K$ and the synchronisation vector $SV_k$ are unchanged (however 
 $j_0$ passes from 
@@
 For each $m\in I_1\uplus I_2$ we have one of the two
-following OT\footnotemark[\thefootnote]:\\
+following OT:\\
 either $m$ in $I_1$
@@
 if we 
-choose\footnotemark[\thefootnote]  $\alpha_Q=\alpha_{j_0}$ and $\Pred\,''= \Pred_{j_0}$. 
+choose  $\alpha_Q=\alpha_{j_0}$ and $\Pred\,''= \Pred_{j_0}$. 
 Considering 
@@
  \end{small}
-\qed
-
-\footnotetext{Cloning and freshness introduce alpha-conversion at many points 
-of the proof; we 
-	only 
-	give major arguments concerning alpha-conversion to make the proof readable; in 
-	general, fresh variables appear in each transition inside
-        terms $\beta_j$, $v$, and 
-	$\Pred$.}
 \end{proof}

### 2020-04-24 2016-Weak-FH-Bisim/WeakBisim.tex
pass on appendix A

@@
 \subsubsection*{ \bf{Lemma~\ref{lem-compose}}:  Open transition composition}~\\
-	Suppose $j_0\in J$ and:\\[-1ex]
+	Consider two pNets $P$ and $Q$ where $P$ is not a pLTS. Suppose $j_0\in J$ and:\\[-1ex]
 \begin{mathpar}
@@
 }%\]
-\text{~~and~~}
+\text{~~\qquad\qquad~and~\qquad\qquad~~}
 %\[
@@
 Note that this does not mean that any two pNets can be composed and produce an open 
-transition. Indeed, the predicate $\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0}$ is not 
+transition. Indeed, the predicate $\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0}$ will not 
 be satisfiable if the action of $\alpha_Q$ cannot be matched with $\beta_{j_0}$.
@@
 \begin{proof} 
-
+Let $P=\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle$.
+Consider first the open transition derived from $P$.
        Consider each premise of the open transition (constructed by \TrDeux\ in 
-Definition~\ref{def:operationalSemantics}). Let $P=\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle$
+Definition~\ref{def:operationalSemantics}). 
 	\begin{small}
@@
 We know each premise is \True\ for $P$ and try to prove the equivalent premise for 
-$P[Q]_{j_0}$ (using the open transition of $Q$). 
+$P[Q]_{j_0}$ (using the open transition of $Q$). $P[Q]_{j_0}$ exhibits a similar \TrDeux rule where
 $K$ and the synchronisation vector are unchanged ($j_0$ is now in the set of sub-pNets); 
@@
     be 
-reduced, we need:\\[-2ex]%\footnote{again we skip arguments related to renaming of fresh 
+reduced, we need:%\footnote{again we skip arguments related to renaming of fresh 
 %variables}:
@@
     		\!\!\!\!\!\Post_m = 	\Post\uplus \Post\,'}$.\\ Finally, the composed open transition can be
-        built by \TrDeux:
-
+        built by \TrDeux\ as follows
 	\noindent
@@
 \end{small}
-        \end{proof}
+   This provides the desired conclusion.     \end{proof}
 
@@
 \end{mathpar}
-Then, we have\\[-1ex]
+Then, for any state $\ostate{s_i^{i\in L_Q}}$ of $Q$, we have\\[-1ex]
 	\[ P[Q]_{j_0}  
@@
  \subsection{Proof of Theorem ~\ref{thm-congr-eq}}
+\noindent{\bf  Congruence}:
+\textit{	Consider an open pNet:
+	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
+	\set{\symb{SV}}\myrangle$.
+	Let $j_0\in J$ be a hole. Let $\pNetQ$ and $\pNetQ'$ be two FH-bisimilar pNets such that 
+	$\Sortop(\pNetQ)=\Sortop(\pNetQ')=\Sort_{j_0}$\footnote{Note that $\Sortop(\pNetQ)=\Sortop(\pNetQ')$ is 
+	ensured by 
+	strong bisimilarity.}. Then 
+	$\pNet[\pNetQ]_{j_0}$ and 
+	$\pNet[\pNetQ']_{j_0}$ are FH-bisimilar.
+}
+\medskip
+\begin{proof}
  The proof of Theorem~\ref{thm-congr-eq} exhibits classically a bisimulation relation for 
@@
  $\mathcal{R}$ that is an FH-bisimulation between the open automata of the two pNets. 
- We will consider the relation\footnote{$\uplus$ is defined on sets as the disjoint union 
- of the contained indexed 
- sets} $\mathcal{R}'=\{(s,t|\Pred_{s,t})|s=s'\uplus s'' \land 
+ We will consider the relation
+%\footnote{$\uplus$ is defined on sets as the disjoint union 
+% of the contained indexed 
+% sets} 
+$\mathcal{R}'=\{(s,t|\Pred_{s,t})|s=s'\uplus s'' \land 
  t=t'\uplus s'' \land s''\in \mathcal{S}_P \land (s',t'|\Pred_{s,t})\in\mathcal{R}\}$ 
@@
 This proves the  condition of the FH-simulation, the other direction is 
- similar.\qed
-
-        \subsection{Proof of Theorem ~\ref{thm-ctxt-eq}}
-
+ similar.
+\end{proof}
+
+        \subsection{Proof of Theorem ~\ref{thm-ctxt-eq}: Context equivalence}
+\textit{	Consider two FH-bisimilar open pNets:
+	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
+	\set{\symb{SV}}\myrangle$ and 	$\pNet' = \mylangle {\pNet'}_i^{i\in I}, 
+	\Sort_j^{j\in 
+	J}, 	\set{\symb{SV'}}\myrangle$ 
+	(recall they must have the same holes to be bisimilar).
+	Let $j_0\in J$ be a hole, and $Q$ be a pNet such that $\Sortop(Q)=\Sort_{j_0}$. Then 
+	$\pNet[Q]_{j_0}$ and 
+	$\pNet'[Q]_{j_0}$ are FH-bisimilar.
+}
+
+\medskip
+
+\begin{proof}
 The proof of Theorem~\ref{thm-ctxt-eq} exhibits  a bisimulation relation for a 
@@
 
- The obtained formula reaches the goal except for two points:\\[-4.3ex] 
+ The obtained formula reaches the goal except for two points:
 \begin{itemize}
@@
 This proves the  condition of the FH-simulation, the other direction is 
-similar.\qed
+similar.
+\end{proof}
 

### 2020-04-24 2016-Weak-FH-Bisim/WeakBisim.tex
preuves un peu mises au propre

@@
 
-\begin{proof} ($\Rightarrow$) We proceed by induction on  $n$ and $m$ (where between each step either $m$ or $n$ increases).
+\begin{proof} ($\Rightarrow$) We present an induction on $n$ and $m$, focusing on the incrementation on $n$: we prove that the property is valid for $-1$, $-1$ prove a general induction for going from $n$ to $n+1$, a similar induction can be applied to go from $m$ to $m+1$
 \begin{itemize}
@@
 \item For the inductive step, first we have by induction hypothesis that the formula holds for some lengths $m$ and $n$.
-Induction step is to infer that formula holds for transitions of length $m+1$ or $n+1$.
-We consider the case $n'=n+1$ (because $m'=m+1$ is similar).
+Induction step is to infer that formula holds for transitions of length  $n+1$.
+We consider the case $n'=n+1$.
 We want to prove (1) $\Rightarrow$ (2) in the lemma, and in (1) we  focus on the case where there is a set of open transitions (this is the case: $s\neq s'$).
@@
 where\\
-$
-\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\!\!\Post_{1j}}}\\
-s''=s_{10} \wedge s_{1(n+2)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
-\displaystyle{
-\set{\gamma}=\mybigdotcup_{i=1}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup}\\
-{}~\qquad \displaystyle{\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
-\\
-\Pred=\bigwedge_{i=1}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{1}\Post_{1j}}\land\\ 
-{}~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}}\Big)\\
-\Post=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}
-$
+\begin{align*}
+s''=s_{10} &\wedge s_{1(n+2)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
+\alpha'=&\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\!\!\Post_{1j}}}\\
+\set{\gamma}=&\mybigdotcup_{i=1}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup\\
+& \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }\\
+\Pred=&\bigwedge_{i=1}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{1}\Post_{1j}}\land\\ 
+&\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}}\Big)\\
+\Post=&\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}
+\end{align*}
 
@@
 where we obtain the conclusion of the lemma, as required with the following assertions (derived from previous assertions):
-\begin{gather*}
-s_{10}=s_{10} \wedge s_{1(n+2)}=s_{2} \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
 \begin{align*}
+s_{10}=s_{10} &\wedge s_{1(n+2)}=s_{2} \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
 \alpha''=&\alpha\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}\subst{\Post_{10}} = \alpha\subst{\bigotimes_{j=n+1}^{0}\Post_{1j}}\\
@@
 \end{align*}
-\end{gather*}
 
@@
 \end{mathpar}
-where\\
-$ 
-s''=s_{30} \wedge s_{3{(m_1+1)}}\!=s''',\quad
-\displaystyle{\set{\gamma_3}= \mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{3 i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{3 j} } }} \\
-\Pred_3\!=\!\bigwedge_{i=0}^{m_1}(\Pred_{3i} \subst{\bigotimes_{j=i-1}^{0}\Post_{3 j}} ),\quad \Post_3= \bigotimes_{i=m_1}^{0} \subst{\Post_{3i}} 
-$
+where
+\begin{mathpar}
+s''=s_{30}
+
+\land
+
+ s_{3{(m_1+1)}}\!=s'''
+
+\land
+
+\displaystyle{\set{\gamma_3}= \mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{3 i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{3 j} } }}
+
+\land
+
+\Pred_3\!=\!\bigwedge_{i=0}^{m_1}(\Pred_{3i} \subst{\bigotimes_{j=i-1}^{0}\Post_{3 j}} )
+
+\land
+
+ \Post_3= \bigotimes_{i=m_1}^{0} \subst{\Post_{3i}} 
+\end{mathpar}
 
@@
 \end{mathpar}
+
 where
-\begin{gather*}
-s'=s_{20} \wedge s_{2(n_2+1)}=s_2 \wedge  s_2' = s_{20}' \wedge s_{2(m_2+1)}'=s''\\
 \begin{align*}
+s'=s_{20} &\wedge s_{2(n_2+1)}=s_2 \wedge  s_2' = s_{20}' \wedge s_{2(m_2+1)}'=s''\\
 \alpha''=&\alpha'\subst{\bigotimes_{j=n_2}^{0}\Post_{2j}}\\
@@
 &\Big(\bigwedge_{i=0}^{m_2}\Pred\,'_{2i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}}\Big)\\
-\Post_2=\bigotimes_{j=m_2}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}
+\Post_2=&\bigotimes_{j=m_2}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}
 \end{align*}
-\end{gather*}
 
@@
 
-such that\\
+such that
 \begin{align*}
@@
 
-Also, we have the following assertions:\\
-$
-{\displaystyle \alpha''=\alpha\subst{\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}\!}\\
-s\!=\!s_{40} \wedge s_{4(n_1+n_2+1)}\!=s_2 \wedge s_2' = s_{50} \wedge s_{5(m_1+m_2+1)}\!=\!s'\\
-\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2} \vis{\set{\beta_{4i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{4 j} } }  \dotcup  \vis{\set{\beta'}\subst{\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}}\dotcup }\\
-{}~\!\qquad\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta_{5i}}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{5i}\shortotimes\Post\,'\shortotimes\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4i}} }
-\\
-\displaystyle{\Pred=
-\bigwedge_{i=0}^{n_1+n_2}\!\!\Pred_{4i}\subst{\bigotimes_{j=i-1}^{0}\Post_{4j}}\land\Pred\,' \subst{\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\!\Post_{4j}}\land}\\ 
-{}~\qquad\quad\bigwedge_{i=0}^{m_1+m_2}\Pred_{5i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{5j}\shortotimes\Post\,'\shortotimes\!\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\!\Post_{4j}}\\
-\Post=\bigotimes_{j=m_1+m_2}^{0}\!\!\!\Post_{5j}\shortotimes\Post\,'\shortotimes\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\Post_{4j}
-$\\
+Also, we have the following assertions:
+\begin{align*}
+s\!=\!s_{40}& \wedge s_{4(n_1+n_2+1)}\!=s_2 \wedge s_2' = s_{50} \wedge s_{5(m_1+m_2+1)}\!=\!s'\\
+\alpha''=&\alpha\subst{\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}\\
+\set{\gamma}=&\mybigdotcup_{i=0}^{n_1+n_2} \vis{\set{\beta_{4i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{4 j} } }  \dotcup  \vis{\set{\beta'}\subst{\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}}\dotcup \\
+&\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta_{5i}}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{5i}\shortotimes\Post\,'\shortotimes\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4i}} }\\
+\Pred=&
+\bigwedge_{i=0}^{n_1+n_2}\!\!\Pred_{4i}\subst{\bigotimes_{j=i-1}^{0}\Post_{4j}}\land\Pred\,' \subst{\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\!\Post_{4j}}\land\\ 
+&\quad\bigwedge_{i=0}^{m_1+m_2}\Pred_{5i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{5j}\shortotimes\Post\,'\shortotimes\!\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\!\Post_{4j}}\\
+\Post=&\bigotimes_{j=m_1+m_2}^{0}\!\!\!\Post_{5j}\shortotimes\Post\,'\shortotimes\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\Post_{4j}
+\end{align*}
+
 This concludes the inductive step, showing  that the decomposition expressed by the $\Leftarrow$ direction of the lemma is always possible with the right side conditions. 

### 2020-04-24 2016-Weak-FH-Bisim/WeakBisim.tex
proof principle double rec

@@
 
-\begin{proof} ($\Rightarrow$) We present an induction on $n$ and $m$, focusing on the incrementation on $n$: we prove that the property is valid for $-1$, $-1$ prove a general induction for going from $n$ to $n+1$, a similar induction can be applied to go from $m$ to $m+1$
+\begin{proof} ($\Rightarrow$) We present an induction on $n$ and $m$, focusing on the incrementation on $n$: we prove that the property is valid for $m=-1$, $n=-1$ apply a first induction proof for going from $n$ to $n+1$, a similar induction can be applied to go from $m$ to $m+1$ (omitted).
 \begin{itemize}

### 2020-04-24 2016-Weak-FH-Bisim/WeakBisim.tex
presentation lemmas 4-5

@@
 
-In this section, we first define two alternative definitions for weak bisimulation.
+In this section, we first define two alternative definitions, one for weak open transition, one for for weak bisimulation.
 We use these two alternative definitions to show that weak bisimulation is an equivalence, we will also re-use these alternative definitions in the  proofs of the theorems in next sections.
@@
 
-\noindent ($\Leftarrow$) We proceed by structural induction on the rules  building  the weak transition. So we consider the different rules:
+\noindent ($\Leftarrow$) We proceed by structural induction on the rules  building  the weak transition (as described in the original definition).
+The recurrence hypothesis being that the  the original definition implies the characterisation (1),with the conditions stated at the bottom of the theorem.
+We consider the different rules:
 
@@
 \begin{align*}
-s\!=\!s_{40}& \wedge s_{4(n_1+n_2+1)}\!=s_2 \wedge s_2' = s_{50} \wedge s_{5(m_1+m_2+1)}\!=\!s'\\
+s\!=\!s_{40}& ~\wedge~s_{4(n_1+n_2+1)}\!=s_2 ~\wedge~s_2' = s_{50} ~\wedge~ s_{5(m_1+m_2+1)}\!=\!s'\\
 \alpha''=&\alpha\subst{\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}\\

### 2020-04-24 2016-Weak-FH-Bisim/WeakBisim.tex
improve equation presentation

@@
 (s_{31},w_{c}|\Pred_{s_{31},c})\in \mathcal{R}$ and \\
- $\Pred_{s_{21},b} \land \Pred_3\implies\\
+ $\Pred_{s_{21},b} \land \Pred_3\implies %\\
 \displaystyle{\bigvee_{c\in C}}
@@
      \Pred_{s_{11},a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$\\
-With the conjunction of the predicate $\Pred_2\subst{\Post_1}$ on both sides of the implication, we get:\\  
-$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies \\
- \displaystyle{\bigvee_{a\in A}}
+With the conjunction of the predicate $\Pred_2\subst{\Post_1}$ on both sides of the implication, we get:
+\begin{multline*}
+(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies \\
+ \bigvee_{a\in A}
   \!\! ( \forall j\in J_a. \vis{\beta_{1j}}\!=\!\gamma_{ja}\!  \land\! \Pred_{OT_a}\! \land\!
-     \Pred_{s_{11},a}\subst{\Post_1\uplus\Post_{OT_a}}) \wedge \Pred_2\subst{\Post_1\uplus\Post_{OT_a}}  
-$
+     \Pred_{s_{11},a}\subst{\Post_1\uplus\Post_{OT_a}}) \wedge \Pred_2\subst{\Post_1\uplus\Post_{OT_a}}  \hspace{-2ex}
+\end{multline*}
 Note that  on the right side of the implication we added  the substitution  of $\Post_{OT_x}$ without affecting the validity of the statement, because  the domain  of the substitution $\Post_{OT_x}$ is disjoint from the others.
-Hence a little rewriting gives:\\
-$(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies\\
-\displaystyle{\bigvee_{a\in A}}
+Hence a little rewriting gives:
+\begin{multline*}
+(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies\\
+\bigvee_{a\in A}
 \!\!   \left(\forall j\in J_a. \vis{\beta_{1j}}\!=\!\gamma_{ja}\land \Pred_{OT_a}
-     \!\land(\Pred_{s_{11},a}\wedge\Pred_2)\subst{\Post_1\uplus\Post_{OT_a}} \right)$\\
+     \!\land(\Pred_{s_{11},a}\wedge\Pred_2)\subst{\Post_1\uplus\Post_{OT_a}} \right)
+\end{multline*}
+
 By replacing the inner predicate $(\Pred_{s_{11},u_a}\wedge\Pred_2)$ by the conclusion of the  statement given in case 2,  the formula becomes: 

### 2020-04-24 2016-Weak-FH-Bisim/WeakBisim.tex
skype comments

@@
 $\subst{y\gets e}$, the operation replaces in a term all occurrences 
-of the variable $y$ by the expression $e$ (note that the absence of binders makes this operation 
-trivial). 
-We use sets of assignments of the form $x_i:=e_i$, ranged over by $\Post$; $\subst{\Post}$ is the substitution that applies all the substitutions defined by $\Post$ in a parallel manner.
-$\otimes$ is the composition operator on substitutions, such that for any term $t$ we have: $t\subst{\Post\shortotimes\Post'} = (t\subst{\Post})\subst{\Post'}$.
+of the variable $y$ by the expression $e$. 
+$\Post$ ranges over (indexed) sets of substitutions; $\subst{\Post}$ is the substitution that applies all the substitutions defined by $\Post$ in a parallel manner.
+$\otimes$ is the composition operator on substitutions, such that for any term $t$ we have: $t\subst{\Post\shortotimes\Post'} = (t\subst{\Post'})\subst{\Post}$.
 
@@
 \begin{itemize}
-\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets indexed over $I$.
+\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets indexed over $I$. $vars(P_i)$ and $vars(P_j)$ must be disjoint for $i\neq j$.
 %  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which sub-pNets are indexed.
@@
 
-\item The set of variables of a pNet $P$, denoted $vars(P)$ is the set of variables of  all pLTSs that compose $P$.
+\item The set of variables of a pNet $P$, denoted $vars(P)$ is disjoint union the set of variables of  all pLTSs that compose $P$.
 
@@
 
-\begin{definition}[Weak open transition]\label{def:weakOT}
+\begin{definition}[Weak open transition (WOT)]\label{def:weakOT}
 A weak open transition over a
@@
 
-\hl{Now focus on OTs}\footnote{In the appendix we use OT to abbreviate ``open transition'' and WOT to stand for ``weak open transition.''} of the subnets.
-For each $m\in I_1\uplus I_2$ we have one of the two
+Now focus on the OTs of the subnets. For each $m\in I_1\uplus I_2$ we have one of the two 
 following OT:\\
@@
 
-\hl{Only elements of} $(I_1\uplus I_2)\backslash\{j_0\}$ and  are useful to assert the premise for reduction of $P$; the last 
+Only elements of $(I_1\uplus I_2)\backslash\{j_0\}$   are useful to assert the premise for reduction of $P$; the last 
 one ensures the open transition for the pNet $Q$ (note that $Q$ is at place $j_0$, and by 
@@
 \end{mathpar}
-where\\
-$
-\displaystyle{\alpha=\alpha'\subst{\bigotimes_{j=n}^{0}\Post_{1j}}}\\
-s=s_{10} \wedge s_{1(n+1)}=s_{20} \wedge s_{21} = s_{30} \wedge s_{3(m+1)}=s'\\
-\displaystyle{
-\gamma_j^{j\in J'}=\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup}\\
-{}~\qquad\qquad\!\displaystyle{\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
+where
+\begin{align*}
+s=s_{10} &\wedge s_{1(n+1)}=s_{20} \wedge s_{21} = s_{30} \wedge s_{3(m+1)}=s'\\
+\alpha=&\alpha'\subst{\bigotimes_{j=n}^{0}\Post_{1j}}\\
+\gamma_j^{j\in J'}=&\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup\\
+&\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }
 \\
-\Pred_{OT}=\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=n}^{0}\Post_{1j}}\land\\ 
-{}~\qquad\qquad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}}\Big)\\
-\Post_{OT}=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}$
+\Pred_{OT}=&\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=n}^{0}\Post_{1j}}\land\\ 
+&\qquad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}}\Big)\\
+\Post_{OT}=&\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}
+\end{align*}
 

### 2020-04-24 2016-Weak-FH-Bisim/WeakBisim.tex
Big changes in use-case texts
Partout sauf les figures !!

@@
 \subsubsection*{Substitutions}
+\label{def:substitutions}
 
@@
 		$\vars(e_b)\!\subseteq\! \vars(s)\cup\vars(\alpha)$, and
-		$\forall j\!\in\! J .\,\left(\vars(e_j)\!\subseteq\! V\cup\vars(\alpha)\land 
+		$\forall j\!\in\! J .\,\left(\vars(e_j)\!\subseteq\! V\cup\iv(\alpha)\land 
 		x_j\!\in V \right)$. %,  and $s= s'\Rightarrow J=\emptyset$.
@@
 of holes, leaves and sorts formalised below in Definition~\ref{def-sortholeleave}.
-Informally, holes are process parameters, leaves provide the set of pLTSs at the leaves of the hierarchical structure of a pNet, and sorts give the signature of a pNete, i.e.
+Informally, holes are process parameters, leaves provide the set of pLTSs at the leaves of the hierarchical structure of a pNet, and sorts give the signature of a pNet, i.e.
 the actions it exposes.
@@
 The $\symb{Sender}$ increments its local error counter $ec$, and resends the message (including $ec$) to the $\symb{Medium}$, that will, eventually, transmit $m,ec$ to the $\symb{Receiver}$.
-Strictly speaking, as variables are local to each  state, we have two distinct $ec$ variables in the \textit{Sender} pLTS, one in state \texttt{s1}, another one in state \texttt{s2}, the value of the variable is updated along the transitions entering each of the two states.
+%Strictly speaking, as variables are local to each  state, we have two distinct $ec$ variables in the \textit{Sender} pLTS, one in state \texttt{s1}, another one in state \texttt{s2}, the value of the variable is updated along the transitions entering each of the two states.
 
@@
 %        $\beta_j$ and $\alpha$, and the state variables of $s$.
-        \Pred\ is a predicate over the  variables $V$ and all variables
+        \Pred\ is a predicate over the  variables in $V$ and all variables
         in the different terms
@@
 allows us to refine the predicate, or substitute any free variable by
-an expression. More formally, let $\Post$ be any substitution and
-$\Pred$ any predicate; suppose $V\cap \dom(\Post)=\emptyset$. Then we have the following
+an expression. More formally, let $\Pred$ be any predicate and $\Post$ any substitution such that $V\cap \dom(\Post)=\emptyset$. Then we have the following
 implication:
@@
 However an open automaton is characterized by a  subset of these open transition which is sufficient to generate, by substitution the other ones.
-In the following, we will abusively write that we define an ``open automaton'' when we provide only the set of open transitions that is sufficient to generate a proper open automaton by saturating each open transition by all possible substitutions.
+In the following, we will abusively write that we define an ``open automaton'' when we provide only the set of open transitions that is sufficient to generate a proper open automaton by saturating each open transition by all possible substitutions and refinements.
 
@@
 
-We define first states of open pNets as tuples of states. We denote them
+We first define states of open pNets as tuples of states. We denote them
  as $\triangleleft\ldots\triangleright$ for distinguishing tuple 
@@
 If the action families do not match or if there is no valuation of
-variables such that the above formula can be ensured the predicate is undefined.
+variables such that the above formula can be ensured then the predicate is undefined.
 
@@
       \{\texttt{P}\mapsto \texttt{p-send(m)}\},  [\texttt{m=m'}],
-        \{\texttt{s1\_msg}\gets \texttt{m}\}
+        \{\texttt{s\_msg}\gets \texttt{m}\}
                       }
@@
     $Post$ uses the variable $\texttt{m}$ from the action of hole $\texttt{P}$ to set the
-    value of the sender state variable named $\texttt{s1\_msg}$.
+    value of the sender variable named $\texttt{s\_msg}$.
 
@@
  %% $  OT_2  = \openrule{
- %%   \emptyset; Pred=[send(SV2\_m)=send(s_1\_m);in(SV2\_m)=in(?m)];  \\ Post=\{m_1\_m:=?m\}
+ %%   \emptyset; Pred=[send(SV\_m)=send(s_\_m);in(SV\_m)=in(?m)];  \\ Post=\{m_\_m:=?m\}
  %%                      }
- %%    {\ostate{s_1,m_0,r_0} \OTarrow{\nounderline{send(SV2\_m)}} \ostate{s_2,m_1,r_0}}
+ %%    {\ostate{s_1,m_0,r_0} \OTarrow{\nounderline{send(SV\_m)}} \ostate{s_2,m_1,r_0}}
  %%    $
@@
  %%     $  OT_2  = \openrule{
- %%      \emptyset; Pred=\True;  \\ Post=\{m_1\_m:=s_1\_m\}
+ %%      \emptyset; Pred=\True;  \\ Post=\{m_\_m:=s_\_m\}
  %%                      }
- %%    {\ostate{s_1,m_0,r_0} \OTarrow{\nounderline{send(s_1\_m)}} \ostate{s_2,m_1,r_0}}
+ %%    {\ostate{s_1,m_0,r_0} \OTarrow{\nounderline{send(s_\_m)}} \ostate{s_2,m_1,r_0}}
  %%    $
@@
  %%    $m_0$ to $m_1$.
- %%    The predicate $Pred$ involves the state variables $s_1\_m$ and
- %%    $s_1\_sb$ of the sender, while the assignment $Post$ sets the
+ %%    The predicate $Pred$ involves the state variables $s_\_m$ and
+ %%    $s_\_sb$ of the sender, while the assignment $Post$ sets the
  %%    state variables of the medium.
@@
 
-%% \LUDO{Je sais pas de quoi parle le prochain todo :-( l'exemple?}
-%% \TODO{Ceci n'est pas nouveau, n'est-ce pas, est-ce utile pour le lecteur ici ? Ou est-ce qu'on bouge tous ces ``details techniques'' dans une annexe ? Si oui, je refais avec un morceau de ABP}
-%% \begin{example} \emph{Using the operational rules to compute
-%%     open-transitions}
-%%   In Fig. \ref{usingrules:OT2} we show the deduction tree used to construct and prove the 
-%%   open transition $OT_2$ of \texttt{EnableCompL} (see example page \pageref{OT:ABP-composed}).
-%%   The rule uses \TrUn\ for the $\delta$ transition of $C_3$, for the $l$ transition of $C_4$, then combines the result using the $a_4$ vector of the bottom pNet node, and the $\nounderline{\delta(x)}$ vector of the top node.
-
-%% \begin{figure}[h]
-%% \begin{mathpar}
-%%   \small
-%%   \inferrule
-%%     {\inferrule
-%%         {0 \xrightarrow {\delta}_{C_3} 1}
-%%         {C_3
-%%           \models
-%%             \openrule{
-%%               0 \xrightarrow {\delta}_{C_3} 1,\,
-%%               \{\xrightarrow{\delta(x_1)}_P\},\,
-%%               v_1=\delta(x_1)}
-%%                       {\ostate{0}\OTarrow{v_1}\ostate{1}}
-%%         }\\
-%% %      \sm{fresh}v         \\
-%%       \inferrule%*[right={L_1}]
-%%         {
-%% %          \sm{fresh}{a_Q} \\
-%%           \inferrule
-%%               {0 \xrightarrow{l}_{C_4} 0}
-%%               % {\ostate{0}\xrightarrow{l}\ostate{0}}
-%%               {C_4
-%%                 \models
-%%                 \openrule{
-%%                       0 \xrightarrow l_{C_4} 0,\,
-%%                       \sm{Pred}_{C_4}}
-%%                       {\ostate{0}\OTarrow{l}\ostate{0}}
-%%               }
-%%         }
-%%         {
-%%           \textrm{Q>>R}\models
-%%               \openrule
-%%                   { 0 \xrightarrow {l}_{C_4} 0,\,
-%%                     \{\xrightarrow{acc(x_2)}_Q\},\,
-%%                     \ v_2=acc(x_2)
-%%                   }
-%%                   {\ostate{0}\OTarrow{v_2}\ostate{0}}
-%%         }   
-%%     }
-%%     {
-%%      \textrm{P>>(Q>>R)}
-%%      \models
-%%      \openrule
-%%          { 0 \xrightarrow{\delta}_{C_3} 1, \\ 0 \xrightarrow{l}_{C_4} 0,\\
-%%            \{\xrightarrow{\delta(x)}_P,\,\xrightarrow{acc(x)}_Q\}, \\
-%%             a_3=v_1 \wedge v=a_3 \wedge x_1=x_2
-%%            }
-%%          {\ostate{00} \OTarrow{v} \ostate{10}}
-%%       }\vspace{-4ex}
-%% \end{mathpar}
-%%   \caption{Proof of transition $OT_2$ (with interaction of processes $P$ and $Q$) for 
-%%   ``P>>(Q>>R)'' \TODO{Change for the new example or remove?}}
-%%   \label{usingrules:OT2}
-%% \end{figure}
-
-%% \end{example}
-
 We have shown in \cite{henrio:Forte2016} that an open-pNet
@@
 Implementation automaton will be labelled $SI_i$. In the figure we
-have annotated each global state with the set of corresponding state variables.
+have annotated each global state with the set of corresponding pLTS variables.
 
@@
 Rule~$\WTDeux$ states that each open transition can be considered as a weak open transition.
-The last rule is the most interesting:  Rule~$\WTTrois$ allows any number of $\tau$ transitions before or after a weak open transition.
+The last rule is the most interesting:  Rule~$\WTTrois$ allows any number of $\tau$ transitions before or after any weak open transition.
 This rules carefully composes predicates, effects, and actions of the holes, indeed in the rule, predicate $\Pred_2$ manipulates variables of $s_1$ that result from the first weak open transition.
-Their value thus depend of the initial state but also of the effect (as a substitution $\Post_1$) of the first weak open transition.
+Their values thus depend on the initial state but also on the effect (as a substitution $\Post_1$) of the first weak open transition.
 In the same manner, $\Pred_3$ must be applied the joint substitution $\Post_2\bigotimes\Post_1$.
@@
 On the top we show the subset of the original open automaton (from Figure \ref{SimpleProtCounter:SpecOA}) considered here, and at the bottom the generated weak transition.
-For reasons of readability, we abbreviate the weak open transitions encoded by $\openrule   {\{\}, True,	() } {s \OTWeakarrow \tau s'}$  as $W_\tau$.
+For readability, we abbreviate the weak open transitions encoded by $\openrule   {\{\}, True,	() } {s \OTWeakarrow \tau s'}$  as $W_\tau$.
 The weak open transition shown here is the transition delivering the result of the algorithm to hole $Q$ by applying rules: \WTUn,\WTDeux, and \WTTrois.
-First rule \WTUn~ adds an $WT_\tau$ loop on each state.
+First rule \WTUn~ adds a $WT_\tau$ loop on each state.
 Rule \WTDeux~ transforms each 3 OTs into WOTs.
@@
          {\{\}, True,
-			(\texttt{ec}\gets \texttt{ec}+1) }
+			(\texttt{b\_ec}\gets \texttt{b\_ec}+1) }
          {\text{b1}\OTWeakarrow \tau \text{b1}}$; $\openrule
          {\{\}, True,
-			(\texttt{ec}\gets \texttt{ec}+1) }
+			(\texttt{b\_ec}\gets \texttt{b\_ec}+1) }
          {\text{b1} \OTWeakarrow \tau \text{b1}}$;  $\openrule
@@
          {\{\}, True,
-			(\texttt{ec}\gets \texttt{ec}+2) }
+			(\texttt{b\_ec}\gets \texttt{b\_ec}+2) }
          {\text{b1} \OTWeakarrow \tau \text{b1}}$. We can  can iterate this construction an arbitrary number of times, getting for any natural number $n$ the weak open transition:
@@
         {\text{b1} \OTWeakarrow \tau \text{b1}} \forall n \geq 0$.
-Finally,  applying again \WTTrois, and using the central open transition having \texttt{\nounderline{out(b1\_m,b1\_ec)}}  as $\alpha$, we get the resulting weak open transition between b1 and b0 (as shown in Figure \ref{WOT2}).
+Finally,  applying again \WTTrois, and using the central open transition having \texttt{\nounderline{out(b\_m,b\_ec)}}  as $\alpha$, we get the resulting weak open transition between b1 and b0 (as shown in Figure \ref{WOT2}).
+Applying the substitutions finaly yields the weak transition $WS_7$ in Figure  \ref{SimpleProtCounter:WeakSpecOA}.
 
@@
 
- For readability, we did not include the full details of the Implementation weak open transitions in Figure \ref{SimpleProtCounter:ImplWOA2}, they will appear below.
-First, we point out that the weak OT loops ($WI_1$,$WI_2$ and $W_\tau$) on state ${000}$ are also present in all other states, we did not repeat them.
-Then many WOTs are similar, and numbered accordingly as 3, 3a, 3b, 3c and 8, 8a, 8b, 8c respectively: they only differ by the name of the state variables in their respective source or target states.
+ For readability, we do not include the full details of the Implementation weak open transitions in Figure \ref{SimpleProtCounter:ImplWOA2}, but we show some examples below and the full list is included in Appendix \ref{}.
+First, let us point out that the weak OT loops ($WI_1$,$WI_2$ and $W_\tau$) on state ${000}$ are also present in all other states, we did not repeat them.
+Then many WOTs are similar, and numbered accordingly as 3, 3a, 3b, 3c and 8, 8a, 8b, 8c respectively: they only differ by the name of the state variables in their respective source or target states; the "variant" WOTs appear in blue in   Figure \ref{SimpleProtCounter:ImplWOA2}.
 \end{example}
@@
 We concentrate on weak open transitions $WI_3$ and $WI_4$.
-Let us denote as $post_n$ the effect (= substitution) of the strong open transitions $OT_n$ from Figure \ref{SimpleProtCounter:ImplOA}:
+Let us denote as $post_n$ the effect (= substitution) of the strong open transitions $SI_n$ from Figure \ref{SimpleProtCounter:ImplOA}:
 \smallskip
 
-$post_3 = (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets 0)$
-
-$post_4 = (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}, \texttt{s2\_ec}\gets \texttt{s1\_ec})$
+$post_3 = (\texttt{s\_msg}\gets \texttt{m}, \texttt{s\_ec}\gets 0)$
+
+$post_4 = (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec})$
 
@@
 
-$post_6 = (\texttt{s1\_ec}\gets \texttt{s2\_ec+1})$
+$post_6 = (\texttt{s\_ec}\gets \texttt{s\_ec+1})$
 
@@
 $post_{456} = post_6 \shortotimes\ post_5 \shortotimes\ post_4
-= (\texttt{s1\_ec}\gets \texttt{s1\_ec}+1)$.
+= (\texttt{s\_ec}\gets \texttt{s\_ec}+1)$.
+\footnote{when showing  the result of $Posts$ composition, we will systematicaly omit the identity substitutions introduced bythe $\shortotimes$ definition in page \pageref{def:substitutions}}
 \medskip
 
-So if we denote ${post_{456*}}$ any iteration of this loop, we get ${post_{456*}} = (\texttt{s1\_ec}\gets \texttt{s1\_ec}+n)$ for any $n\ge 0$, and the \Post~ of the weak OT  $WI_{3}$ is:\\
- ${post_{456*}}\shortotimes\ post_3 = (\texttt{s1\_msg}\gets m, \texttt{s1\_ec}\gets n), \forall n\ge 0$ and \Post~ of  $WI_{3a}$  is:\\ $post_4\shortotimes {post_{456*}}\shortotimes\ post_3 = (\texttt{m1\_msg}\gets m, \texttt{m1\_ec}\gets n), \forall n\ge 0$.
+So if we denote ${post_{456*}}$ any iteration of this loop, we get ${post_{456*}} = (\texttt{s\_ec}\gets \texttt{s\_ec}+n)$ for any $n\ge 0$, and the \Post~ of the weak OT  $WI_{3}$ is:\\
+ $Post_3 = post_{456*}\shortotimes\ post_3 = (\texttt{s\_msg}\gets m, \texttt{s\_ec}\gets n), \forall n\ge 0$ and \Post~ of  $WI_{3a}$  is:\\ $post_4\shortotimes {post_{456*}}\shortotimes\ post_3 = (\texttt{m\_msg}\gets m, \texttt{m\_ec}\gets n), \forall n\ge 0$.
 \medskip
@@
   {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
-    (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets n)}
+    (\texttt{s\_msg}\gets \texttt{m}, \texttt{s\_ec}\gets n)}
   {000 \OTWeakarrow {\nounderline{\texttt{in(m)}}} 100}
@@
          {\{\}, True, 
-   (\texttt{m1\_msg}\!\gets\! \texttt{s1\_msg}, \texttt{m1\_ec}\!\gets\! \texttt{s1\_ec}+n, \texttt{s2\_ec}\!\gets\! \texttt{s1\_ec}+n)}
+   (\texttt{m\_msg}\!\gets\! \texttt{s\_msg}, \texttt{m\_ec}\!\gets\! \texttt{s\_ec}+n, \texttt{s\_ec}\!\gets\! \texttt{s\_ec}+n)}
          {100 \OTWeakarrow {\tau} 210}
@@
          {\{\}, True, 
-    (\texttt{s1\_ec}\gets \texttt{s1\_ec}+n)}
+    (\texttt{s\_ec}\gets \texttt{s\_ec}+n)}
   {100 \OTWeakarrow {\tau} 100}
@@
 \begin{array}{ll}
-Post_{6a}= post_{4}\shortotimes\ post_{456*}\shortotimes\ post_{6} =&  (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}, \texttt{s2\_ec}\gets \texttt{s1\_ec})\,
-\shortotimes \\ &(\texttt{s1\_ec}\gets \texttt{s1\_ec}+n) 
-\shortotimes (\texttt{s1\_ec}\gets \texttt{s2\_ec}+1) =\\
-&(\texttt{m1\_msg}\!\gets \texttt{s1\_msg}, \texttt{m1\_ec}\!\gets \texttt{s2\_ec}+1\!+\!n, \texttt{s2\_ec}\!\gets \texttt{s2\_ec}+1\!+\!n)
+Post_{6a}= post_{4}\shortotimes\ post_{456*}\shortotimes\ post_{6} =&  (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec})\,
+\shortotimes \\ &(\texttt{s\_ec}\gets \texttt{s\_ec}+n) 
+\shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+1) =\\
+&(\texttt{m\_msg}\!\gets \texttt{s\_msg}, \texttt{m\_ec}\!\gets \texttt{s\_ec}+1\!+\!n, \texttt{s\_ec}\!\gets \texttt{s\_ec}+1\!+\!n)
 \end{array}$\\
@@
          {\{\}, True, 
-         (\texttt{m1\_ec}\gets \texttt{s1\_ec}+1+n, \texttt{s2\_ec}\gets \texttt{s2\_ec}+1+n)}
+         (\texttt{m\_ec}\gets \texttt{s\_ec}+1+n, \texttt{s\_ec}\gets \texttt{s\_ec}+1+n)}
          {220 \OTWeakarrow {\tau} 210} \forall n\ge 0
@@
 $Post_{8c}= post_{8}\shortotimes\ post_{7}\shortotimes\ post_{4}\shortotimes\ post_{456*} 
-= (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_msg}+1+n), \forall n\ge 0$
+= (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_msg}+1+n), \forall n\ge 0$
 
@@
 $ WI_{8c}(n) = \openrule
-         {\{\texttt{Q}\mapsto \texttt{q-recv(s1\_msg,s2\_ec}+n)\}, True, ()}
-         {210 \OTWeakarrow {\nounderline{\texttt{out(r1\_msg,r1\_ec)}\subst{(\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_msg}+n)}}} 202}\forall n\ge 0
+         {\{\texttt{Q}\mapsto \texttt{q-recv(s\_msg,s\_ec}+n)\}, True, ()}
+         {210 \OTWeakarrow {\nounderline{\texttt{out(r\_msg,r\_ec)}\subst{(\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_msg}+n)}}} 202}\forall n\ge 0
         $
@@
     b0 & $202$ & True\\
-    b1 & $100$ & $\texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec}$\\
-    b1 & $210$ & $\texttt{b1\_msg = m1\_msg} \land \texttt{b1\_ec = m1\_ec}$\\
-    b1 & $220$ & $\texttt{b1\_msg = s2\_msg} \land \texttt{b1\_ec = s2\_ec}$\\
-    b1 & $201$ & $\texttt{b1\_msg = r1\_msg} \land \texttt{b1\_ec = r1\_ec}$\\
+    b1 & $100$ & $\texttt{b\_msg = s\_msg} \land \texttt{b\_ec = s\_ec}$\\
+    b1 & $210$ & $\texttt{b\_msg = m\_msg} \land \texttt{b\_ec = m\_ec}$\\
+    b1 & $220$ & $\texttt{b\_msg = s\_msg} \land \texttt{b\_ec = s\_ec}$\\
+    b1 & $201$ & $\texttt{b\_msg = r\_msg} \land \texttt{b\_ec = r\_ec}$\\
     \hline
@@
   {\{\texttt{P}\mapsto \texttt{p-send(m1)}\}, True,
-    (\texttt{b1\_msg}\gets \texttt{m1}, \texttt{b1\_ec}\gets 0)}
+    (\texttt{b\_msg}\gets \texttt{m1}, \texttt{b\_ec}\gets 0)}
   {\text{b0} \OTarrow {\nounderline{\texttt{in(m1)}}} \text{b1}}
@@
   {\{\texttt{P}\mapsto \texttt{p-send(m2)}\}, True,
-    (\texttt{s1\_msg}\gets \texttt{m2}, \texttt{s1\_ec}\gets 0)}
+    (\texttt{s\_msg}\gets \texttt{m2}, \texttt{s\_ec}\gets 0)}
   {000 \OTWeakarrow {\nounderline{\texttt{in(m2)}}} 100}
@@
   \item Their sets of active (non-silent) holes is the same: $J' = J_x = \{\texttt{P}\}$.
-  \item Triple ($\text{b1},  100,  \texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec}$) is in $\mathcal{R}$.
+  \item Triple ($\text{b1},  100,  \texttt{b\_msg = s\_msg} \land \texttt{b\_ec = s\_ec}$) is in $\mathcal{R}$.
   \item The verification condition \\
@@
 \\
-(\texttt{b1\_msg\!\!
-= \!\!s1\_msg} \land \texttt{b1\_ec\!\!
+(\texttt{b\_msg\!\!
+= \!\!s\_msg} \land \texttt{b\_ec\!\!
 =\!\!
-s1\_ec}) \subst{(\texttt{b1\_msg}\!\gets\!
-\texttt{m1}, \texttt{b1\_ec}\!\gets\!
-0)\uplus (\texttt{s1\_msg}\!\gets\!
-\texttt{m2},\texttt{s1\_ec}\!\gets\!
+s\_ec}) \subst{(\texttt{b\_msg}\!\gets\!
+\texttt{m1}, \texttt{b\_ec}\!\gets\!
+0)\uplus (\texttt{s\_msg}\!\gets\!
+\texttt{m2},\texttt{s\_ec}\!\gets\!
 0)})\}$
@@
   $ SI_{4} = \openrule
-         {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}, \texttt{s2\_ec}\gets \texttt{s1\_ec})}
+         {\{\}, True, (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec}, \texttt{s\_ec}\gets \texttt{s\_ec})}
          {100 \OTarrow {\tau} 210}
@@
   $ WS_4(n) = \openrule
-         {\{\}, True, (\texttt{b1\_ec}\gets \texttt{b1\_ec}+n)}
+         {\{\}, True, (\texttt{b\_ec}\gets \texttt{b\_ec}+n)}
          {\text{b1} \OTWeakarrow {\tau} \text{b1}}
@@
 
-  \medskip       A similar reasonning gives us\TODO{Refait, please check. But I think it does not show much more than first case, can we find a better case ?}
-
+  \medskip       A similar reasonning gives us
 \begin{itemize}
   \item No active holes and the pair of ressulting states $<210,b1>$ is in $\mathcal{R}$.
-\item $fv(SI_4) = \{\}, fv(WS_4(n)) = \{n\}$, \TODO{Is that correct ? Is it true that considering $n$ as a free variable allows Z3 to find  a suitable value...?}
+\item $fv(SI_4) = \{\}, fv(WS_4(n)) = \{n\}$,
 \item and the verification condition\\
 
-         $(\texttt{b1\_msg} = \texttt{s1\_msg} \land \texttt{b1\_ec} = \texttt{s1\_ec}) \land True\hspace{3mm} \implies
-\exists n.(True \land \tau=\tau \land \\ (\texttt{b1\_msg} = \texttt{m1\_msg} \land \texttt{b1\_ec} = \texttt{m1\_ec})  \subst{\texttt{m1\_msg}\!\gets\!
-\texttt{s1\_msg}, \texttt{m1\_ec}\!\gets\!
-\texttt{s1\_ec}, \texttt{s2\_ec}\gets \texttt{s1\_ec}}
-\uplus \subst{\texttt{b1\_ec}\gets \texttt{b1\_ec}+n})
+         $(\texttt{b\_msg} = \texttt{s\_msg} \land \texttt{b\_ec} = \texttt{s\_ec}) \land True\hspace{3mm} \implies
+\exists n.(True \land \tau=\tau \land \\ (\texttt{b\_msg} = \texttt{m\_msg} \land \texttt{b\_ec} = \texttt{m\_ec})  \subst{\texttt{m\_msg}\!\gets\!
+\texttt{s\_msg}, \texttt{m\_ec}\!\gets\!
+\texttt{s\_ec}, \texttt{s\_ec}\gets \texttt{s\_ec}}
+\uplus \subst{\texttt{b\_ec}\gets \texttt{b\_ec}+n})
 $
@@
 %% - a tau-loop on each state
-%% - a transition from <s0\_a0\_r0> to <s2\_a1\_r0>, resulting from the sequence OT\-1;OT\-6 followed by any number of the loop (OT\_9;ot\_12;OT\_6).
+%% - a transition from <s0\_a0\_r0> to <s\_a\_r0>, resulting from the sequence OT\-1;OT\-6 followed by any number of the loop (OT\_9;ot\_12;OT\_6).
 %%
-%%Many weak should be added, e.g. Tau loops on states <s2\_a1\_r0>, <s2\_a2\_r0>, 
-%%<s2\_a0\_r0>, encoding the loop.
-
-\begin{figure}[h]
-   \centerline{\includegraphics[width=10cm]{XFIG/SimpleProtImpl-WOA}}
-  \caption{Weak Open Automaton of the implementation}
-   \label{Appendix:ImplOA}
-\end{figure}
+%%Many weak should be added, e.g. Tau loops on states <s\_a\_r0>, <s\_a\_r0>, 
+%%<s\_a0\_r0>, encoding the loop.
+
+% \begin{figure}[h]
+%   \centerline{\includegraphics[width=10cm]{XFIG/SimpleProtImpl-WOA}}
+%   \caption{Weak Open Automaton of the implementation}
+ %   \label{Appendix:ImplOA}
+% \end{figure}
 
 In Figure \ref{Appendix:ImplOA} we show the weak open automaton of our implementation pNet.
-\TODO{This version is very uncomplete, at least 12 WOTs are missing, including: all variants of WI3 starting from 202; the inverse of WI4, WI5, WI6, WI8, etc}
-\TODO{See also the last bunch of ransitions, at the end of the list, for combinations of any $\tau$ transition with an external action of P or Q}
-
-\begin{figure}[h]
-   \centerline{\includegraphics[width=11cm]{XFIG/SimpleProtImpl-WOA2}}
-  \caption{Weak Open Automaton of the implementation: alternative}
-   \label{Appendix:ImplOA2}
-\end{figure}
-
-Figure \ref{Appendix:ImplOA2} shows a more compact version of this weak automation, that will be easier to read for humans...
+
 It is based on the observation that states 202 and 000 are only linked by a "pure $\tau$" transition, and have exactly the same possible behaviors.
@@
   {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
-    (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets n)}
+    (\texttt{s\_msg}\gets \texttt{m}, \texttt{s\_ec}\gets n)}
   { \{000,202\} \OTWeakarrow {\nounderline{\texttt{in(m)}}} 100}
@@
   {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
-    (\texttt{m1\_msg}\gets \texttt{m}, \texttt{m1\_ec}\gets n, \texttt{s2\_ec}\gets n)}
+    (\texttt{m\_msg}\gets \texttt{m}, \texttt{m\_ec}\gets n, \texttt{s\_ec}\gets n)}
   { \{000,202\} \OTWeakarrow {\nounderline{\texttt{in(m)}}} 210}
@@
   {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
-    (\texttt{s2\_ec}\gets n)}
+    (\texttt{s\_ec}\gets n)}
   { \{000,202\} \OTWeakarrow {\nounderline{\texttt{in(m)}}} 220}
@@
   {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
-    (\texttt{r1\_msg}\gets \texttt{m}, \texttt{r1\_ec}\gets n)}
+    (\texttt{r\_msg}\gets \texttt{m}, \texttt{r\_ec}\gets n)}
   { \{000,202\} \OTWeakarrow {\nounderline{\texttt{in(m)}}} 201}
@@
          {\{\}, True, 
-   (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n, \texttt{s2\_ec}\gets \texttt{s1\_ec}+n)}
+   (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec}+n, \texttt{s\_ec}\gets \texttt{s\_ec}+n)}
          {100 \OTWeakarrow {\tau} 210}
@@
          {\{\}, True, 
-    (\texttt{s2\_ec}\gets \texttt{s1\_ec}+n)}
+    (\texttt{s\_ec}\gets \texttt{s\_ec}+n)}
          {100 \OTWeakarrow {\tau} 220}
@@
 $ WI_5(n) = \openrule
-         {\{\}, True, (\texttt{s2\_ec}\gets \texttt{s2\_ec}+n)}
+         {\{\}, True, (\texttt{s\_ec}\gets \texttt{s\_ec}+n)}
          {210 \OTWeakarrow {\tau} 220}
@@
 $ WI_{5a}(n) = \openrule
-         {\{\}, True, (\texttt{s1\_ec}\gets \texttt{s2\_ec}+1+n)}
+         {\{\}, True, (\texttt{s\_ec}\gets \texttt{s\_ec}+1+n)}
          {210 \OTWeakarrow {\tau} 100}
@@
 $ WI_6(n) = \openrule
-         {\{\}, True, (\texttt{s1\_ec}\gets \texttt{s2\_ec}+1+n)}
+         {\{\}, True, (\texttt{s\_ec}\gets \texttt{s\_ec}+1+n)}
          {220 \OTWeakarrow {\tau} 100}
@@
          {\{\}, True, 
-         (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s2\_ec}+1+n, \texttt{s2\_ec}\gets \texttt{s2\_ec}+1+n)}
+         (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec}+1+n, \texttt{s\_ec}\gets \texttt{s\_ec}+1+n)}
          {220 \OTWeakarrow {\tau} 210}
@@
 
-$Post_{6a}=\ post_{4}\shortotimes\ Post_{456}^*\shortotimes\ post_{6}\\
-= \left( (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}, \texttt{s2\_ec}\gets \texttt{s1\_ec})
-\shortotimes (\texttt{s1\_ec}\gets \texttt{s1\_ec}+n) \right)
-\shortotimes (\texttt{s1\_ec}\gets \texttt{s2\_ec}+1) \\
-= (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets (\texttt{s2\_ec}+1)+n, \texttt{s2\_ec}\gets (\texttt{s2\_ec}+1)+n)$
+$Post_{6a}=\ post_{4}\shortotimes\ post_{456}^*\shortotimes\ post_{6}\\
+= \left( (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec})
+\shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+n) \right)
+\shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+1) \\
+= (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets (\texttt{s\_ec}+1)+n, \texttt{s\_ec}\gets (\texttt{s\_ec}+1)+n)$
 
 \medskip
-This result ($WI_{6a}$) is INCORRECT: the Post cannot use $s1\_msg$, this variable is not available in state 220
-
 $ WI_{456*}(n) = \openrule
          {\{\}, True, 
-    (\texttt{s1\_msg}\gets \texttt{s1\_msg}, \texttt{s1\_ec}\gets \texttt{s1\_ec}+n)}
+    (\texttt{s\_ec}\gets \texttt{s\_ec}+n)}
   {100 \OTWeakarrow {\tau} 100}
@@
 
-Note that the loop itself does not assign $s1\_msg$, but as we are in a self-loop of state 100, we can add the identity assignment on it.
-\medskip
-
 $ WI_{564*}(n) = \openrule
          {\{\}, True, 
-    (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{s2\_ec}\gets \texttt{s2\_ec}+1+n, \texttt{m1\_ec}\gets \texttt{s2\_ec}+1+n)}
+    (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{s\_ec}\gets \texttt{s\_ec}+1+n, \texttt{m\_ec}\gets \texttt{s\_ec}+1+n)}
   {210 \OTWeakarrow {\tau} 210}
@@
 
-Because
-
-$Post_{564}=\ post_{4}\shortotimes\ post_{6}\shortotimes\ post_{5}\\
-= \left( (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}, \texttt{s2\_ec}\gets \texttt{s1\_ec})
-\shortotimes (\texttt{s1\_ec}\gets \texttt{s2\_ec}+1) \right)
-\shortotimes () \\
-= (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s2\_ec}+1, \texttt{s2\_ec}\gets \texttt{s2\_ec}+1$
-
-This result is INCORRECT: the Post cannot use $s1\_msg$, this variable is not available in state 210
-
 $ WI_{645*}(n) = \openrule
          {\{\}, True, 
-    (\texttt{s2\_ec}\gets \texttt{s2\_ec}+1+n)}
+    (\texttt{s\_ec}\gets \texttt{s\_ec}+1+n)}
   {220 \OTWeakarrow {\tau} 220}
@@
 $ WI_7(n) = \openrule
-         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_ec}+n)}
+         {\{\}, True, (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_ec}+n)}
          {210 \OTWeakarrow {\tau} 201}
@@
 
-$WI_{7a}$ shows the same problem, as it  includes a dependency on $s1\_msg$:
-
 $ WI_{7a}(n) = \openrule
-         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{m1\_ec}+n)}
+         {\{\}, True, (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{m\_ec}+n)}
          {220 \OTWeakarrow {\tau} 201}
@@
 $ WI_{7b}(n) = \openrule
-         {\{\}, True, (\texttt{r1\_msg}\gets \texttt{m1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_ec}+n)}
+         {\{\}, True, (\texttt{r\_msg}\gets \texttt{m\_msg}, \texttt{r\_ec}\gets \texttt{s\_ec}+n)}
          {100 \OTWeakarrow {\tau} 201}
          \ \forall n\ge 1$
-
-\RAB{Erreur sur les deux transition $WI_{7}$, $WI_{7a}$ et $WI_{7b}$}
 
@@
 $ WI_{8a}(n) = \openrule
-         {\{\texttt{Q}\mapsto \texttt{q-recv(m1\_msg,m1\_ec}+n)\}, True, ()}
-         {210 \OTWeakarrow {\nounderline{\texttt{out(m1\_msg,m1\_ec}+n)}} \{202, 000\}}
+         {\{\texttt{Q}\mapsto \texttt{q-recv(m\_msg,m\_ec}+n)\}, True, ()}
+         {210 \OTWeakarrow {\nounderline{\texttt{out(m\_msg,m\_ec}+n)}} \{202, 000\}}
          \ \forall n\ge 1$
@@
  $ WI_{8b}(n) = \openrule
-         {\{\texttt{Q}\mapsto \texttt{q-recv(??\_msg,s2\_ec}+n)\}, True, ()}
-         {220 \OTWeakarrow {\nounderline{\texttt{out(??\_msg,m2\_ec}+n)}} \{202, 000\}}
+         {\{\texttt{Q}\mapsto \texttt{q-recv(??\_msg,s\_ec}+n)\}, True, ()}
+         {220 \OTWeakarrow {\nounderline{\texttt{out(??\_msg,m\_ec}+n)}} \{202, 000\}}
          \ \forall n\ge 1$
@@
  $ WI_{8c}(n) = \openrule
-         {\{\texttt{Q}\mapsto \texttt{q-recv(s1\_msg,s1\_ec}+n)\}, True, ()}
-         {100 \OTWeakarrow {\nounderline{\texttt{out(s1\_msg,s1\_ec}+n)}} \{202, 000\}}
+         {\{\texttt{Q}\mapsto \texttt{q-recv(s\_msg,s\_ec}+n)\}, True, ()}
+         {100 \OTWeakarrow {\nounderline{\texttt{out(s\_msg,s\_ec}+n)}} \{202, 000\}}
          \ \forall n\ge 1$
-
-%$Post_{8'''}= post_{8}\shortotimes\ post_{7}\shortotimes\ post_{4}\shortotimes\ Post_{456}^*\shortotimes\ post_{6} = (\texttt{r1\_msg}\gets \texttt{s1\_msg}, \texttt{r1\_ec}\gets \texttt{s2\_msg}+1+n), \forall n\ge 0$
 
@@
          {\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], 
-   (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n, \texttt{s2\_ec}\gets \texttt{s1\_ec}+n)}
+   (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec}+n, \texttt{s\_ec}\gets \texttt{s\_ec}+n)}
          {100 \OTWeakarrow {\texttt{p-a}} 210}
@@
          {\{\texttt{Q}\mapsto \texttt{q-b}\}, [\forall \texttt{m,ec}. \texttt{q-b} \neq \texttt{q-recv(m,ec)} ],
-   (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}+n, \texttt{s2\_ec}\gets \texttt{s1\_ec}+n)}
+   (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec}+n, \texttt{s\_ec}\gets \texttt{s\_ec}+n)}
          {100 \OTWeakarrow {\texttt{q-b}} 210}
@@
         {\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], 
-    (\texttt{s1\_msg}\gets \texttt{s1\_msg}, \texttt{s1\_ec}\gets \texttt{s1\_ec}+n)}
+    (\texttt{s\_msg}\gets \texttt{s\_msg}, \texttt{s\_ec}\gets \texttt{s\_ec}+n)}
   {100 \OTWeakarrow {\texttt{p-a}} 100}
         $
-
-%\TODO{ajouter les boucles de $WI_1$ et $WI_2$, dans le cas ou $p_a$ (resp $q_b$) sont des $\tau$:}
-%
-%$WI_{12*}(n) = \openrule
-%{\{(\texttt{P}\mapsto \tau|\texttt{Q}\mapsto \tau)^n\},true, ()}
-%  {s \OTWeakarrow {\tau} s} 
-%s \in S$
 
@@
 
-We reacall here the realtion $\mathcal{R}$ that is the candidate for our weak bisimulation relation:
+We recall here the relation $\mathcal{R}$ that is the candidate for our weak bisimulation relation:
 

### 2020-04-27 2016-Weak-FH-Bisim/WeakBisim.tex
petites corrections

@@
 	}\]
-\TODO{j'ai du mal, je reviens}
 
@@
 leaves): $\Post=\Post\,'\uplus \Post\,''$. This concludes the 
-proof as we checked all the premises of the open transition for both $P$ and $Q$. We obtain the following reduction by the rule \TrDeux
+proof as we checked all the premises of the open transition for both $P$ and $Q$. We obtain the following reduction by the rule \TrDeux:
 	\noindent
@@
 \end{mathpar}
-Then, we have\\[-2ex]
+Then, we have:\\[-2ex]
 	\[ P[Q]_{j_0}  
@@
 We know each premise is \True\ for $P$ and try to prove the equivalent premise for 
-$P[Q]_{j_0}$ (using the open transition of $Q$). $P[Q]_{j_0}$ exhibits a similar \TrDeux rule where
+$P[Q]_{j_0}$ (using the open transition of $Q$). $P[Q]_{j_0}$ exhibits a similar \TrDeux~rule where
 $K$ and the synchronisation vector are unchanged ($j_0$ is now in the set of sub-pNets); 
@@
 
- Let $A_1 = <\!J,\mathcal{S}_1, s_0,
-    \mathcal{T}_1\!>$ and $A_2 = <\!J,\mathcal{S}_2,t_0,  \mathcal{T}_2\!>$ be open automata; $<\!J,\mathcal{S}_1, s_0,
-    \WT_1\!>$ and $<\!J,\mathcal{S}_2,t_0,  \WT_2\!>$ be the
+ Let $A_1 = <\!J,\mathcal{S}_1, s_0, V_1,
+    \mathcal{T}_1\!>$ and $A_2 = <\!J,\mathcal{S}_2,t_0, V_2, \mathcal{T}_2\!>$ be open automata; $<\!J,\mathcal{S}_1, s_0,V_1,
+    \WT_1\!>$ and $<\!J,\mathcal{S}_2,t_0, V_2, \WT_2\!>$ be the
 weak open automata derived from $A_1$ and $A_2$ respectively.
@@
 And thus, because $\beta_{pj}^{j\in J\cap \Holes(Q)}$ are equal to the concatenation of  $(\beta'_{1pj})^{j\in J\cap \Holes(Q)}$, $(\beta'_{2j})^{j\in J\cap \Holes(Q)}$, and $(\beta_{3pj}')^{j\in J\cap \Holes(Q)}$ (re-indexed because we skipped some transitions), and additionally $(\beta_{1pj}')^{j\in J\cap \Holes(Q)}$, $(\beta_{2j}')^{j\in J\cap \Holes(Q)}$, and $(\beta_{3pj}')^{j\in J\cap \Holes(Q)}$ are identical to the hole labels $\beta_{1kj}^{j\in J\cap \Holes(Q)}$, $\beta_{2j}^{j\in J\cap \Holes(Q)}$, and $\beta_{3kj}^{j\in J\cap \Holes(Q)}$ (re-indexed) when $Q$ moves\footnote{more precisely, when $Q$ moves either $\beta_{1kj}^{j\in J\cap \Holes(Q)}$ is not empty  and thus $(\beta_{1pj}')^{j\in J\cap \Holes(Q)}=\beta_{1kj}^{j\in J\cap \Holes(Q)}$, or both are empty if the holes of $Q$ perform no action}.
-We can assert a similar equality on postconditions, i.e.
+We can assert a similar equality on post-conditions, i.e.
 between $\Post\,''_p$ and $\Post\,''_{1k}$, $\Post\,''_{2}$, $\Post\,''_{3k}$ where $\Post\,''_{1p}$ is the restriction of $\Post_{1p}$ over variables of $\Leaves(Q)$ (see initial decomposition, case 1, 2, and 3 above).
 Overall, we have
-
 $\forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i$ (see above)\\
@@
 \end{mathpar}
-such that
+such that\\
 
@@
 
-\noindent Note that we have $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$
+\noindent Note that we have $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$.
 
@@
 \end{lemma}
-
+~~\\
 \begin{proof} Suppose we have:
@@
 $\gamma_{j_0}=[\beta_0..\beta_n]\\
-~~\quad =\displaystyle{\mybigdotcup_{\substack{i=0\\j_0\in J_{1i}}}^{m_1} \vis{{\beta_{1ij_0}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \dotcup \vis{{\beta_{2j_0}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}}\, \dotcup \\
-~\qquad\quad\displaystyle{ \mybigdotcup_{\substack{i=0\\j_0\in J_{3i}}}^{m_2} \vis{{\beta_{3ij_0}} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}}$\\
+\mbox{~~}\quad =\displaystyle{\mybigdotcup_{\substack{i=0\\j_0\in J_{1i}}}^{m_1} \vis{{\beta_{1ij_0}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \dotcup \vis{{\beta_{2j_0}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}}\, \dotcup \\
+\mbox{~~~~}\qquad\displaystyle{ \mybigdotcup_{\substack{i=0\\j_0\in J_{3i}}}^{m_2} \vis{{\beta_{3ij_0}} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}}$\\
 
@@
 \]
-and thus we also have a weak OT by definition \ref{def:buildweakOT} (rule (\WTDeux)):
+and thus we also have a weak OT by definition \ref{def:buildweakOT} (rule \WTDeux):
 \[P[Q]_{j_0} \models\openrule
@@
 It is still possible to glue them together in a global rules with two more terms for $\Pred$ and $\Post$ terms.
-This global merge is possible because the postconditions of $P$ only act on variables of $P$ and those of $Q$ on variables of $Q$ (for example $\Post_i$ has no effect on $\Pred_{1p}$ and thus does not need to be taken into account when dealing with WOTs where $Q$ does not move).
+This global merge is possible because the post-conditions of $P$ only act on variables of $P$ and those of $Q$ on variables of $Q$ (for example $\Post_i$ has no effect on $\Pred_{1p}$ and thus does not need to be taken into account when dealing with WOTs where $Q$ does not move).
 
@@
 
-Finally, concerning postconditions:
+Finally, concerning post-conditions:
 {\footnotesize \begin{equation*}

### 2020-04-28 2016-Weak-FH-Bisim/WeakBisim.tex
small typos

@@
 
-%\begin{figure}[h]
-%   \centerline{\includegraphics[width=13cm]{ATG/SPSpecWeakOpen}}
-%  \caption{Weak Open Automaton of the Specification \TODO{out of date}}
-%   \label{SimpleProtCounter:WeakSpecOA}
-%\end{figure}
-
 \begin{figure}[h]
@@
 
- For readability, we do not include the full details of the Implementation weak open transitions in Figure \ref{SimpleProtCounter:ImplWOA2}, but we show some examples below and the full list is included in Appendix \ref{}.
+ For readability, we do not include the full details of the Implementation weak open transitions in Figure \ref{SimpleProtCounter:ImplWOA2}, but we show some examples below and the full list is included in Appendix \ref{Appendix:FullExample}.
 First, let us point out that the weak OT loops ($WI_1$,$WI_2$ and $W_\tau$) on state ${000}$ are also present in all other states, we did not repeat them.
@@
 We can now show some of the weak OTs of Figure \ref{SimpleProtCounter:ImplWOA2} (the full table is included in Appendix \ref{Appendix:FullExample}) :
+
+\TODO{Qu'est-ce qu'on avait dit ici pour "$n$" ? a droite ou a gauche, mais pas les deux ?Et est-ce qu'on le laisse en italique dans les expressions, pour souligner son statut de parametre ?.
+Dans tous les cas expliquer ?}
 \smallskip
@@
          {\{\}, True, 
-         (\texttt{m\_ec}\gets \texttt{s\_ec}+1+n, \texttt{s\_ec}\gets \texttt{s\_ec}+1+n)}
+         (\texttt{m\_ec}\gets \texttt{s\_ec}+1+n, \texttt{s\_ec}\gets \texttt{s\_ec}+n)}
          {220 \OTWeakarrow {\tau} 210} \forall n\ge 0
@@
 $ WI_{8c}(n) = \openrule
-         {\{\texttt{Q}\mapsto \texttt{q-recv(s\_msg,s\_ec}+n)\}, True, ()}
-         {210 \OTWeakarrow {\nounderline{\texttt{out(r\_msg,r\_ec)}\subst{(\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_msg}+n)}}} 202}\forall n\ge 0
+         {\{\texttt{Q}\mapsto \texttt{q-recv(s\_msg,s\_ec}+n)\}, True, (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_msg}+1+n)}
+         {210 \OTWeakarrow {\nounderline{\texttt{out(s\_msg,s\_ec}+n)}} 202}\forall n\ge 0
         $
@@
 
-% \begin{figure}[h]
-%   \centerline{\includegraphics[width=10cm]{XFIG/SimpleProtImpl-WOA}}
-%   \caption{Weak Open Automaton of the implementation}
- %   \label{Appendix:ImplOA}
-% \end{figure}
-
-In Figure \ref{Appendix:ImplOA} we show the weak open automaton of our implementation pNet.
+\begin{figure}[h]
+   \centerline{\includegraphics[width=10cm]{XFIG/SimpleProtImpl-WOA2}}
+   \caption{Weak Open Automaton of the implementation}
+   \label{Appendix:ImplOA2}
+ \end{figure}
+
+In Figure \ref{Appendix:ImplOA2} we recall the weak open automaton of our implementation pNet.
 

### 2020-04-28 2016-Weak-FH-Bisim/WeakBisim.tex
variable simplification everywhere

@@
 		\Post\,''$ where $\Post\,''$ is the restriction of $\Post$ over variables of 
-		$\Leaves(Q)$.
+		$Q$.
 \end{lemma}
@@
 More precisely, we state that $\tau$ is not observable if the automaton always allows any $\tau$ transition from holes, and additionally the global transition resulting from a $\tau$ action of a hole is a $\tau$ transition not changing the pNet's state.
-We define $\Id(s)$ as the identity function on variables of state s.
+We define $\Id(V)$ as the identity function on variables of $V$.
 \begin{definition}[Non-observability of $\tau$ actions]\label{def:Non-ObsTau}
@@
          {
-           (j\mapsto\tau),\True,\Id(s)}
+           (j\mapsto\tau),\True,\Id(V)}
          {s \OTarrow {\tau} s}
@@
          {s \OTarrow {\alpha} s'}
-         \in \mathcal{T} \] If there exists $j$ such that $\beta_j=\tau$ then we have: \[ \alpha=\tau\land s=s'\land \Pred=\True\land\Post=\Id(s) \land J=\{j\}
+         \in \mathcal{T} \] If there exists $j$ such that $\beta_j=\tau$ then we have: \[ \alpha=\tau\land s=s'\land \Pred=\True\land\Post=\Id(V) \land J=\{j\}
 \]
@@
 		\land \Pred\,''\land \alpha_Q=\beta_{j_0}$, $\Post=\Post\,'\uplus 
-		\Post\,''$ where $\Post\,''$ is the restriction of $\Post$ over variables of 
-		$\Leaves(Q)$.
+		\Post\,''$ where $\Post\,''$ is the restriction of $\Post$ over variables  
+		$\vars(Q)$.
 
@@
  \land \Pred\,''\land \alpha_Q= \beta_{j_0}$, $\Post_{OT}=\Post\,'\uplus 
- \Post\,''$ ($\Post\,''$ is the restriction of $\Post$ over variables of 
- $\Leaves(Q)$). As $Q$ is FH-bisimilar to $Q'$ and $(\ostate{s_{i}^{i \in 
+ \Post\,''$ ($\Post\,''$ is the restriction of $\Post$ over $\vars(Q)$). As $Q$ is FH-bisimilar to $Q'$ and $(\ostate{s_{i}^{i \in 
  		L}},\ostate{{t}_{i}^{i \in L'}}|\Pred_{s,t})\in\mathcal{R}$ there is a family 
@@
 		\land \Pred\,''\land \alpha_Q=\beta_{j_0}$, $\Post_{OT}=\Post\,'\uplus 
-			\Post\,''$ ($\Post\,''$ is the restriction of $\Post$ over variables of 
-			$\Leaves(Q)$). As $P$ is FH-bisimilar to $P'$ and $(\ostate{s_{i}^{i \in 
+			\Post\,''$ ($\Post\,''$ is the restriction of $\Post$ over $\vars(Q)$). As $P$ is FH-bisimilar to $P'$ and $(\ostate{s_{i}^{i \in 
 			L}},\ostate{{t}_{i}^{i \in L'}}|\Pred_{s,t})\in\mathcal{R}$ there is a family 
@@
 		\end{mathpar} 
-where $\Post_p$ only act upon variables of 
-		$\Leaves(Q)$.
+where for any $p$, $\Post_p$ only acts upon  variables $\vars(Q)$.
 \end{lemma}
@@
 where\\
- for all $l\in L$: $s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
-$\alpha=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}}$\\
-$\displaystyle{
-\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\! \Post_{1j}}}\dotcup\  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}}} \dotcup \\ 
-{}~\quad\,\qquad \displaystyle{\mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }}
+{\small \begin{align*}
+\forall l\in L.\,&s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l\\
+\alpha=&\alpha'{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}}\\
+\gamma_j^{j\in J}=&\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\! \Post_{1j}}}\dotcup\  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup  
+{\mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }}
 \\
-\Pred=\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\land\\ 
-{}~\qquad\quad\bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
-\Post=\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}$\\
+\Pred=&\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\land
+\bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
+\Post=&\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}
+\end{align*}}
 
@@
 $\Pred_{1p} \!\!\iff\!\!
-{\Pred\,'_{1p}}\land {\Pred\,''_{1p}}\land\alpha_{1p}\!=\!\beta_{1pj_0}$, $\Post_{1p}\!=\!{\Post\,'_{1p}}\uplus{\Post\,''_{1p}}$  where ${{\Post\,''_{1p}}}$ is the restriction of $\Post_{1p}$ over variables of $\Leaves(Q)$.\\
+{\Pred\,'_{1p}}\land {\Pred\,''_{1p}}\land\alpha_{1p}\!=\!\beta_{1pj_0}$, $\Post_{1p}\!=\!{\Post\,'_{1p}}\uplus{\Post\,''_{1p}}$  where ${{\Post\,''_{1p}}}$ is the restriction of $\Post_{1p}$ over   $\vars(Q)$.\\
 Else $Q$ does not move and we have: \\
@@
 		\land {\Pred\,''_2}\land \alpha_2=\beta_{2j_0}$, $\Post_2={\Post\,'_2}\uplus 
-		{\Post\,''_2}$ where ${\Post\,''_2}$ is the restriction of $\Post_2$ over variables of $\Leaves(Q)$.
+		{\Post\,''_2}$ where ${\Post\,''_2}$ is the restriction of $\Post_2$ over variables  $\vars(Q)$.
 
@@
 We can assert a similar equality on post-conditions, i.e.
-between $\Post\,''_p$ and $\Post\,''_{1k}$, $\Post\,''_{2}$, $\Post\,''_{3k}$ where $\Post\,''_{1p}$ is the restriction of $\Post_{1p}$ over variables of $\Leaves(Q)$ (see initial decomposition, case 1, 2, and 3 above).
+between $\Post\,''_p$ and $\Post\,''_{1k}$, $\Post\,''_{2}$, $\Post\,''_{3k}$ where $\Post\,''_{1p}$ is the restriction of $\Post_{1p}$ over $\vars(Q)$ (see initial decomposition, case 1, 2, and 3 above).
 Overall, we have
@@
 Finaly, we list here in raw format, the 19 OTs computed by the tool for the SimpleProtImpl pNet.
-This view uses variable names very close to the internal representation in the tool, allowing for tracability of generated fresh variables. For example:
+This view uses variable names very close to the internal representation in the tool, allowing for traceability of generated fresh variables. For example:
 \begin{itemize}

### 2020-04-28 2016-Weak-FH-Bisim/WeakBisim.tex
corrections mineures dans les annexes

@@
 $\alpha=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}}\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,''_{1j}}}=\alpha''\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,''_{1j}}}$.\\
-As $\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,''_{1j}}}$ has no effect on variables of $P$ and thus on variables of $\alpha$, so we have $\alpha=\alpha''$.
+As $\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,''_{1j}}}$ has no effect on variables of $P$ and thus on variables of $\alpha''$, so we have $\alpha=\alpha''$.
 \\
-For all $l\in L$: 
-$s_l=s_{0l} \wedge s_{(m_1+1)l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)l}=s'_l$
-and \\%$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\}$,\\
-${(\gamma_j')}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}}} \dotcup\\
-{}~~\qquad \qquad\qquad\qquad\qquad \mybigdotcup_{i=0}^{m_2}
-\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}} }\\
-\Pred\,'=\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}\land\\ 
-{}~\qquad\qquad\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}\\
-\Post'=\bigotimes_{j=m_2}^{0}\!\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}$
+{\small \begin{align*}
+\forall l\in L.\,&s_l=s_{0l} \wedge s_{(m_1+1)l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)l}=s'_l\\
+{(\gamma_j')}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}=&\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}}} \dotcup\\
+& \mybigdotcup_{i=0}^{m_2}
+\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}} }
+\\
+\Pred\,'=&\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}\land\\ 
+&\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}\\
+\Post'=&\bigotimes_{j=m_2}^{0}\!\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}
+\end{align*}}
 
@@
 \begin{small}
-$\forall p\! \in\! [0..n_1] Q\models{\openrule
+$\forall p\! \in\! [0..n_1]~ Q\models{\openrule
 			{
@@
 				}%\]
-,$  
+,~~$  
 $ Q\models{\openrule
@@
 and \\
-$\forall p \in [0..n_2] Q\models{\openrule
+$\forall p \in [0..n_2]~ Q\models{\openrule
 			{
@@
 \\ 
-such that $n_1 \leq m_1$ and $n_2 \leq m_2$.\\
+such that $n_1 \leq m_1$ and $n_2 \leq m_2$.
+
 By renaming all state names ($s$, $u$ and $t$) with the same state name $v$. We have:
@@
 \begin{small}
-$\forall p\! \in\! [n'_{k}..(n_k\!-\!1)] Q\models{\openrule
+$\forall p\! \in\! [n'_{k}..(n_k\!-\!1)]~ Q\models{\openrule
 			{

### 2020-05-09 2016-Weak-FH-Bisim/WeakBisim.tex
More small things and presentation on appendix

@@
 
+\TODO{Ludo: add positioning wrt FORTE (variables)}
+
 \subsection{Notations}
@@
 \section{A model of process composition}\label{sec:OT}
+
+\TODO{Ludo: add positioning wrt FORTE (variables)}
 
@@
 This concludes the inductive step, showing  that the decomposition expressed by the $\Leftarrow$ direction of the lemma is always possible with the right side conditions. 
+\qedhere
 \end{itemize}
@@
 With:
-$\forall l \in L_Q. v_{kl}=v_{(n'_{k})l} \wedge v_{kl}'=v_{(n'_k)l}$\\
-$\alpha_k'=\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}}$\\
-$\displaystyle{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=\displaystyle{\mybigdotcup_{i=n'_{k}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}} \dotcup\\
-{}~~\qquad \qquad\qquad\mybigdotcup_{i=n_k+1}^{n'_{k+1}-1}
+{\small
+\begin{align*}
+\forall l \in L_Q. &v_{kl}=v_{(n'_{k})l} \wedge v_{kl}'=v_{(n'_k)l}\\
+\alpha_k'=&\alpha_{n_k}{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}}\\
+{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=&{\mybigdotcup_{i=n'_{k}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}} \dotcup\\
+&\mybigdotcup_{i=n_k+1}^{n'_{k+1}-1}
 \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}} \subst{\bigotimes_{l=i-1}^{n_k\!+\!1}\!\Post\,''_{l}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}} }\\
-%
-\Pred_k=\bigwedge_{i=n'_{k}}^{n_k\!-\!1}\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\Pred\,''_{n_k} \subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\\ 
-{}~\qquad\quad\bigwedge_{i=n_k+1}^{n'_{k+1}-1}\!\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\!\Post\,''_{j}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{j}}
+\Pred_k=&\bigwedge_{i=n'_{k}}^{n_k\!-\!1}\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\Pred\,''_{n_k} \subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\\ 
+&\bigwedge_{i=n_k+1}^{n'_{k+1}-1}\!\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\!\Post\,''_{j}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{j}}
 \\
-\Post_k= \bigotimes_{j=n'_{k+1}-1}^{n'_{k}}\!\!\Post\,''_{j}$\\
+\Post_k= &\bigotimes_{j=n'_{k+1}-1}^{n'_{k}}\!\!\Post\,''_{j}
+\end{align*}
+}
 
@@
 
-We need now to show that this set of WOT verifies the conditions of the lemma, i.e. it is a set of WOT of the form:
+We need now to show that the set of WOT obtained above verifies the conditions of the lemma, i.e. it is a set of WOT of the form:
 \[	Q\models{\openrule
@@
 Overall, we have
-$\forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i$ (see above)\\
+$\forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i$ (see above):\\
 {\scriptsize \begin{equation*}
@@
 }
-$\Pred = \displaystyle{\Pred\,'
-		\land \!\!\bigwedge_{p=0}^n((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} )}$\\
+Next, we have
+\[\Pred = \displaystyle{\Pred\,'
+		\land \!\!\bigwedge_{p=0}^n((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} )}\]
 Indeed,
-\begin{small}
+\begin{scriptsize}
 \begin{equation*}
@@
 \end{split}\end{equation*}
-\end{small}
-which is exactly what is needed.\\
+\end{scriptsize}
+which is exactly what is needed.
+
 Finally we have~~
@@
 because
-\begin{equation*}
-\begin{split}
+{\small \begin{align*}
 \Post&=\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}\\
 &=\bigotimes_{j=m_2}^{0}\!\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j} \uplus \bigotimes_{j=m_2}^{0}\!\!\Post\,''_{3j}\shortotimes\Post\,''_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,''_{1j}\\
-&=\Post\,' \uplus \bigotimes_{j=n'_{n+1}-1}^{0}\!\!\Post\,''_{j}
-\end{split}
-\end{equation*}
+&=\Post\,' \uplus \bigotimes_{j=n'_{n+1}-1}^{0}\!\!\Post\,''_{j}\qedhere
+\end{align*}}
 %
@@
 \end{mathpar}
-Let\\[-3ex] 
-\begin{mathpar}
+Let 
 %J_Q=\displaystyle{\bigcup_{t=0}^nJ_{t}}
-%\qquad
-\Pred\,'=\Pred\land (\beta_{j_0}=\alpha_Q\land \Pred_Q) \quad\text{~~and~~}\quad
+\qquad
+$\Pred\,'=\Pred\land (\beta_{j_0}=\alpha_Q\land \Pred_Q) \quad\text{~~and~~}\quad
 %\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
 \Post\,'=\Post\uplus\Post_Q
-\end{mathpar}
-Then, we have\\[-3ex]
-	\[ P[Q]_{j_0}  
+$
+
+Then, we have
+{\small	\[ P[Q]_{j_0}  
 	\models
@@
 	}
-	\]
+	\]}
 \end{lemma}
 \begin{proof}
-By  Lemma \ref{lem-rel-OT-WOT} we can decompose the WOT of $Q$ into  a series of $k+1$ and $k'+1$ tau open transitions and an observable open transition:
+By  Lemma \ref{lem-rel-OT-WOT} we can decompose the WOT of $Q$ into  a series of $k+1$ and $k'+1$ tau open transitions and an $\alpha'_Q$ open transition (that can be observable or not depending on $\alpha_Q$):
 \begin{mathpar}
@@
 
-\item For the observable open transition.  By Lemma \ref{lem-compose} with the lemma hypotheses we obtain:\\ 
+\item For the possibly observable open transition.  By Lemma \ref{lem-compose} with the lemma hypotheses we obtain:\\ 
 	\[ P[Q]_{j_0}  
@@
 $\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$
-and $\alpha=\alpha'$  because $\Post_{1j}$ acts on variables of $Q$ and $\alpha$ contains only variables of $P$.\\
-$\displaystyle{
-\set{\gamma_c}=\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{i=h-1}^{0}\!\!
-\Post_{1i} } }  \dotcup  \vis{({\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2})\subst{\bigotimes_{i=k}^{0}\Post_{1i}}} \dotcup}$ \\
-${}~~\hspace{1.8em}\displaystyle{\mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{i=h-1}^{0}\!\!\Post_{3i}\shortotimes\Post_2\shortotimes\bigotimes_{i=k}^{0}\Post_{1i}} }}$\\
-${}~~\hspace{0.6em}=\set{\gamma}\uplus\vis{\beta_j^{\in J\setminus \{j_0\}}} \quad$  because $\Post_{1j}$  does not act on variables of $\beta_j$.  \\
+and $\alpha=\alpha'$  because $\Post_{1j}$ acts on variables of $Q$ and $\alpha$ contains only variables of $P$.
 \begin{small}
-$\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_{1i}}\land
-\left(Pred\land\Pred_2\land \alpha'_Q=\beta_{j_0 }\right)\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land\\\displaystyle
-\bigwedge_{h=0}^{k'}{\Pred_{3h}}\subst{\bigotimes_{i=h-1}^{0}{\Post_{3i}}\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}
-\end{array}
-$\\
-$\Post_c=\displaystyle{(\bigotimes_{i=k'}^{0}{\Post_{3i}})\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}$
+\begin{align*}
+\set{\gamma_c}=&\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{i=h-1}^{0}\!\!
+\Post_{1i} } }  \dotcup  \vis{({\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2})\subst{\bigotimes_{i=k}^{0}\Post_{1i}}} \dotcup\\
+&\mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{i=h-1}^{0}\!\!\Post_{3i}\shortotimes\Post_2\shortotimes\bigotimes_{i=k}^{0}\Post_{1i}} }\\
+=&\set{\gamma}\uplus\vis{\beta_j^{\in J\setminus \{j_0\}}} \quad  \text{ because $\Post_{1j}$  does not act on variables of $\beta_j$.}  
+\\
+\Pred_c=&
+\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_{1i}}\land
+\left(Pred\land\Pred_2\land \alpha'_Q=\beta_{j_0}\right) \subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land\\
+&\bigwedge_{h=0}^{k'}{\Pred_{3h}}\subst{\bigotimes_{i=h-1}^{0}{\Post_{3i}}\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}
+\\
+\Post_c=&(\bigotimes_{i=k'}^{0}{\Post_{3i}})\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}
+\end{align*}
 \end{small}
-
 \noindent Note that we have $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$.
 
-Note also that $\Post$ only acts on variables of $P$ while $\Post_{1i}$ only acts on state variables of $Q$.
+Note also that $\Post$ only acts on variables of $P$ while $\Post_{1i}$ only acts on  variables of $Q$.
 We conclude on predicate and posts as follows\footnote{$\Post_{1i}$ only has an effect on variables of $Q$ and thus does not modify $\Pred$ or $\beta_{j_0}$}:
@@
 &=\Pred_Q\land\Pred\land \alpha_Q=\beta_{j_0}\\[.3ex]
-\Post_c&=\Post\uplus\Post_Q \\[-3ex]
+\Post_c&=\Post\uplus\Post_Q \qedhere
 \end{split}

### 2020-05-11 2016-Weak-FH-Bisim/WeakBisim.tex
more cleanup

@@
 \end{proof}
-
+\smallskip
 \begin{lemma}[Weak open transition composition]\label{lem-Weakcompose} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
@@
 		\ostate{s_i'^{\, i\in L}}}
-}\\
-\text{~~and for all $p\in[0..n]$~~}
+}
+\qquad\text{~~and for all $p\in[0..n]$~~}\quad
 Q\models{\openrule
@@
 J_Q=\displaystyle{\bigcup_{p=0}^nJ_{p}}
-\qquad
+
+\forall{i\in L_Q}.\,s_i=s_{0i}~~\land~~s'_i=s_{(n+1) i}
+
+\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}\subst{\bigotimes_{k=p}^{0}{\Post_k}}}
+
 \Pred\,'=\Pred\land \bigwedge_{p=0}^{n}(\alpha_t=\beta_t\land \Pred_t)\bigotimes_{i=p-1}^{0}\Post_i
-\\
-\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}\subst{\bigotimes_{k=p}^{0}{\Post_k}}}\text{\quad and\quad}
+
 \Post\,'=\Post\uplus\bigotimes_{p=n}^{0}
 		\Post_p
-\\
-\forall{i\in L_Q}.\,s_i=s_{0i} \text{\quad and \quad} \forall {i\in L_Q}.\,s'_i=s_{(n+1) i}
-\end{mathpar}
-Then, we have\\[-2ex]
+\end{mathpar}
+Then, we have
 	\[ P[Q]_{j_0}  
@@
 %\end{mathpar}
-\noindent where for all $i\in L$:\\
-$s_i=s_{10 i} \wedge s_{1(m_1+1) i}=s_{20i} \wedge  s_{21i}= s_{30 i} \wedge s_{3(m_2+1) i}=s'_i$\\
-$\alpha=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}}$ \\
-%\begin{multline*}
-$\gamma_j^{j\in J}=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \dotcup \, \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}}\, \dotcup\\
-{}~\qquad\quad \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{3p}} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}$\\
-%\end{multline*}
-%\begin{multline*}
-$\Pred=\displaystyle{\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\big)\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land}$\\ 
-${}~~\qquad\quad\displaystyle{\bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}}$\\
-$\Post=\displaystyle{\bigotimes_{p=m_2}^{0}\Post_{3p}\otimes\Post_2\otimes\bigotimes_{j=m_1}^{0}\Post_{1j}}$\\
-%\end{multline*}
+\noindent where:
+{\small\begin{align*}
+\forall i\in L.~~s_i=s_{10 i} &\wedge s_{1(m_1+1) i}=s_{20i} \wedge  s_{21i}= s_{30 i} \wedge s_{3(m_2+1) i}=s'_i\\
+\alpha=&\alpha'{\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \\
+\gamma_j^{j\in J}=&{\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \dotcup \, \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}}\, \dotcup\\
+&\mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{3p}} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}\\
+\Pred=&{\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\big)\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land}\\ 
+&{\bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}}\\
+\Post=&{\bigotimes_{p=m_2}^{0}\Post_{3p}\otimes\Post_2\otimes\bigotimes_{j=m_1}^{0}\Post_{1j}}
+\end{align*}
+}
 
@@
 which the hole $j_0$ moves in the 3 sets of OTs above ($\beta_m$ is the action that matches the hole $j_0$ in the OT $\alpha'$), in other words, we have for all $i$, $\beta_{1 n_i j_0}$ a visible action, as additionally:\\
+{\small
 $\gamma_{j_0}=[\beta_0..\beta_n]\\
-\mbox{~~}\quad =\displaystyle{\mybigdotcup_{\substack{i=0\\j_0\in J_{1i}}}^{m_1} \vis{{\beta_{1ij_0}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \dotcup \vis{{\beta_{2j_0}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}}\, \dotcup \\
-\mbox{~~~~}\qquad\displaystyle{ \mybigdotcup_{\substack{i=0\\j_0\in J_{3i}}}^{m_2} \vis{{\beta_{3ij_0}} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}}$\\
+\mbox{~~}\quad =
+\displaystyle{\mybigdotcup_{\substack{i=0\\j_0\in J_{1i}}}^{m_1} \vis{{\beta_{1ij_0}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \dotcup \vis{{\beta_{2j_0}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}}\, \dotcup \\
+\mbox{~~~~}\qquad \displaystyle{ \mybigdotcup_{\substack{i=0\\j_0\in J_{3i}}}^{m_2} \vis{{\beta_{3ij_0}} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}}$}
 

### 2020-05-11 2016-Weak-FH-Bisim/WeakBisim.tex
polish appendix encore

@@
 \begin{scriptsize}
-\begin{equation*}
-\begin{split}
+\begin{align*}
 \Pred&\iff\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\land
@@
 &\qquad\land\bigwedge_{i=0}^{m_2} \left(\Pred\,'_{3i}
-		\land {\Pred\,''_{3i}}\land \alpha_{3i}=\beta_{3ij_0}\right) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
+		\land {\Pred\,''_{3i}}\land \alpha_{3i}=\beta_{3ij_0}\right) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\displaybreak[0]\\
 &\iff\bigwedge_{i=0}^{m_1}\left((\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{1j}})
@@
 (\gamma_{j_0}=[\alpha'_{i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{j}}|i\in[0..n]])
-\end{split}\end{equation*}
+\end{align*}
 \end{scriptsize}
@@
 =&\set{\gamma}\uplus\vis{\beta_j^{\in J\setminus \{j_0\}}} \quad  \text{ because $\Post_{1j}$  does not act on variables of $\beta_j$.}  
-\\
+\displaybreak[0]\\
 \Pred_c=&
@@
 \end{small}
-~~\\
 %\end{mathpar}
-\noindent where:
+
+ where:
 {\small\begin{align*}
@@
 {\small
-$\gamma_{j_0}=[\beta_0..\beta_n]\\
+$\gamma_{j_0}=~[\beta_0..\beta_n]\\
 \mbox{~~}\quad =
-\displaystyle{\mybigdotcup_{\substack{i=0\\j_0\in J_{1i}}}^{m_1} \vis{{\beta_{1ij_0}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \dotcup \vis{{\beta_{2j_0}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}}\, \dotcup \\
+\displaystyle{\mybigdotcup_{\substack{i=0\\j_0\in J_{1i}}}^{m_1} \vis{{\beta_{1ij_0}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \,\dotcup\, \vis{{\beta_{2j_0}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}}\, \,\dotcup \\
 \mbox{~~~~}\qquad \displaystyle{ \mybigdotcup_{\substack{i=0\\j_0\in J_{3i}}}^{m_2} \vis{{\beta_{3ij_0}} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}}$}
@@
 \noindent We have, by definition of $n_i$ and $n'_i$:\\
-$\displaystyle{\forall{i\in[0..m-1]}, \beta_{1 n_i j_0}\subst{\bigotimes_{k=n_i-1}^{0}\Post_{1k}}=\beta_i}$, $\displaystyle{\beta_{2 j_0}\subst{\bigotimes_{k=m_1}^{0} \Post_{1k} }=\beta_m}$, and \\
-$\displaystyle{\forall{i\in[m+1..n]}, \beta_{3 n_i' j_0}\subst{\bigotimes_{k=n_i'-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}=\beta_i}$\\
-
-\noindent Now, we compose OTs for each of the case above (OTs of $P$):
+$\displaystyle{\forall{i\in[0\,..\,m\!-\!1]}, \beta_{1 n_i j_0}\subst{\bigotimes_{k=n_i-1}^{0}\Post_{1k}}=\beta_i}$, \qquad$\displaystyle{\beta_{2 j_0}\subst{\bigotimes_{k=m_1}^{0} \Post_{1k} }=\beta_m}$, and \\
+$\displaystyle{\forall{i\in[m\!+\!1\,..\,n]}, \beta_{3 n_i' j_0}\subst{\bigotimes_{k=n_i'-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}=\beta_i}$\\
+
+\noindent Now, we compose OTs for each of the case above (depending on the OT of $P$):
 \begin{enumerate}
-\item For the first $\tau$ OTs, i.e, $p\in [0..m_1]$. We have: \\
+\item For the first $\tau$ OTs, i.e, $p\in [0\,..\,m_1]$. We have: \\
 Either there is $i$ such that $p=n_i$, and thus $\beta_i$ and $\beta_{1 p j_0}$ are defined. In this case by Lemma~\ref{lem-Weakcompose1},  we have: 
@@
 	\]
-with \\
-
-$ \set{\gamma'_{1p}}=\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{1pj}^{j\in J_{1p}\setminus \{j_0\}}},
-\Pred\,'_{1p}=\Pred_{1p}\land (\beta_{1pj_0}=\alpha_i\land \Pred_i)$, and\\
-
-$ \Post\,'_{1p}=\Post_{1p}\uplus\Post_i$\\
+with 
+\begin{mathpar}
+ \set{\gamma'_{1p}}=\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{1pj}^{j\in J_{1p}\setminus \{j_0\}}}
+
+\Pred\,'_{1p}=\Pred_{1p}\land (\beta_{1pj_0}=\alpha_i\land \Pred_i)
+
+ \Post\,'_{1p}=\Post_{1p}\uplus\Post_i
+\end{mathpar}
 
@@
          {	\set{\gamma'_2},\Pred\,'_2,\Post\,'_2 }
-         {\ostate{{s_{20j}}^{j\in L}\uplus s_{mj}^{j\in L_Q}}\OTWeakarrow {\alpha'} \ostate{{(s_{21j})}^{j\in L}\uplus s_{(m+1)j}^{j\in L_Q}}}\]
-with\\
-
-$\set{\gamma'_2}=\gamma_{m j}^{j\in J_m}\uplus\vis{\beta_{2j}^{j\in J_2\setminus \{j_0\}}},
-\Pred\,'_{2}=\Pred_{2}\land (\beta_{2j_0}=\alpha_m\land \Pred_m)$, and\\
-
-$\Post\,'_{2}=\Post_{2}\uplus\Post_m$\\
-
-\item For the last $\tau$ OTs, i.e, $p\in [0..m_2]$. We have similarly to the first case:\\
+         {\ostate{{(s_{20j})}^{j\in L}\uplus (s_{mj})^{j\in L_Q}}\OTWeakarrow {\alpha'} \ostate{{(s_{21j})}^{j\in L}\uplus (s_{(m+1)j})^{j\in L_Q}}}\]
+with
+\begin{mathpar}
+\set{\gamma'_2}=\gamma_{m j}^{j\in J_m}\uplus\vis{\beta_{2j}^{j\in J_2\setminus \{j_0\}}}
+
+\Pred\,'_{2}=\Pred_{2}\land (\beta_{2j_0}=\alpha_m\land \Pred_m)
+
+\Post\,'_{2}=\Post_{2}\uplus\Post_m
+\end{mathpar}
+
+\item For the last $\tau$ OTs, i.e, $p\in [0\,..\,m_2]$. We have similarly to the first case:\\
  Either there is $i$ such that $p=n'_i$, and thus $\beta_i$ and $\beta_{1 p j_0}$ are defined. In this case by Lemma~\ref{lem-Weakcompose1}, we have: 
@@
 	\]
-with\\
-
-$\set{\gamma'_{3p}}=\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{3pj}^{j\in J_{3p}\setminus \{j_0\}}}, 
+with
+\begin{mathpar}
+\set{\gamma'_{3p}}=\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{3pj}^{j\in J_{3p}\setminus \{j_0\}}}
+
 \Pred\,'_{3p}=\Pred_{3p}\land (\beta_{3pj_0}=\alpha_i\land \Pred_i)
-$ and,\\
-
-$\Post\,'_{3p} =\Post_{3p}\uplus\Post_i$\\
+
+\Post\,'_{3p} =\Post_{3p}\uplus\Post_i
+\end{mathpar}
 
@@
 	\]
-Where\\
-{\small $
-\alpha''=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}\\
-\displaystyle{
-\set{\gamma'}=
+Where
+{\small 
+\begin{align*}
+\alpha''=&\alpha'{\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}\\
+\set{\gamma'}=&
  \mybigdotcup_{i=0}^{m_1}\set{\gamma'_{1i}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{1k}}\,\dotcup\,
@@
  \mybigdotcup_{i=0}^{m_2}\set{\gamma'_{3i}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}
-}
-\\
-\Pred\,''=\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\ 
-{}~\qquad\qquad\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_2}^{0}\Post\,'_{1j}}\\
-\Post\,''=\bigotimes_{j=m_2}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}
-$
+\displaybreak[0]\\
+\Pred\,''=&\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\ 
+&\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_2}^{0}\Post\,'_{1j}}\displaybreak[0]\\
+\Post\,''=&\bigotimes_{j=m_2}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}
+\end{align*}
 }
@@
 \begin{footnotesize}
-\begin{equation*}
-\begin{split}
+\begin{align*}
 \Pred\,''&=\Big(\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\ &\qquad
 ~\quad\bigwedge_{i=0}^{m_3}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\Big)\\
-&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\
-&\qquad \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\Big)%\\&\qquad
-\land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i\\&\qquad
+&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}\land\Pred_2\subst{\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\Big)\\&\qquad
+\land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i%\\&\qquad
 \land \Big( \bigwedge_{i=0}^{m-1}(\beta_{1{n_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j={n_i}-1}^{0}\Post\,'_{1j}}\land(\beta_{2{j_0}}=\alpha_m) \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\ &\qquad
-~\quad\bigwedge_{i=m+1}^{n}(\beta_{3{n'_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j=n'_i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\Big)\\
-&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\big)\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\&\qquad \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\Big)%\\&\qquad
-\land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i\\&\qquad
+~\quad\bigwedge_{i=m+1}^{n}(\beta_{3{n'_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j=n'_i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\Big)\displaybreak[0]\\
+&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}\big)\land\Pred_2\subst{\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\Big)\\&\qquad
+\land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i
 \land \Big(\bigwedge_{i=0}^{m-1}(\beta_{i}=\alpha_i)\subst{\bigotimes_{j={i-1}}^{0}\Post_{j}}\land(\beta_m=\alpha_m )\subst{\bigotimes_{j=m}^{0}\Post_{j}}\land\\ &\qquad
@@
 &=\Pred
-\end{split}
-\end{equation*}
+\end{align*}
 \end{footnotesize}

### 2020-05-12 2016-Weak-FH-Bisim/WeakBisim.tex
appendix

@@
 \begin{small}
-$\forall p\!\in\![0..m_1].P\models\openrule
+$\forall p\!\in\![0\,..\,m_1].P\models\openrule
     {{\beta_{1pj}^{j\in J_{1p}}},\Pred_{1p},\Post_{1p}   }
@@
 \\
-and  $\forall p \in [0..m_2].P\models\openrule
+and  $\forall p \in [0\,..\,m_2].P\models\openrule
          {
@@
 However it must be noticed that in steps 1 and 3, we have two kinds of WOTs with different signatures (depending on whether $Q$ moves or not).
-It is still possible to glue them together in a global rules with two more terms for $\Pred$ and $\Post$ terms.
+It is still possible to glue them together in a global rule with two more terms for $\Pred$ and $\Post$ terms.
 This global merge is possible because the post-conditions of $P$ only act on variables of $P$ and those of $Q$ on variables of $Q$ (for example $\Post_i$ has no effect on $\Pred_{1p}$ and thus does not need to be taken into account when dealing with WOTs where $Q$ does not move).
@@
 We now  compare each element of the obtained WOT with the conclusion of the lemma:
-\begin{align*}
+{\small \begin{align*}
 \alpha''&=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}}\\
@@
 & = \alpha
-\end{align*}
+\end{align*}}
 
 For $\set{\gamma'}$ we distinguish elements in the holes of $P$ and of $Q$.
+
  First suppose $j\in J\setminus\{j_0\}$ we have $\gamma'_j=\gamma_j$ because $\Post'_{ij}$ has no effect on variables of $P$ and on $\beta_{1pj}$, consequently\\
-\begin{equation*}
-\begin{split}\gamma'_j=&\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \dotcup  \vis{{\beta_{2j}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}\, \dotcup\\
-&
+{\small \begin{equation*}
+\begin{split}\gamma'_j=&\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}}\subst{\bigotimes_{k=i-1}^{0}\! \Post_{1k} } }  \dotcup  \vis{{\beta_{2j}}\subst{\bigotimes_{k=m_1}^{0}\!\Post_{1k}}}\, \dotcup
 \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}
@@
 \end{equation*}
-
-Now, when $j\in J_t$ for some $t$,  $\gamma'_j$ is the concatenation of elements of $\gamma'_{1ij}$, $\gamma'_{2 j}$, $\gamma'_{3ij}$  that are not empty.
+}
+
+Second, when $j\in J_t$ for some $t$,  $\gamma'_j$ is the concatenation of elements of $\gamma'_{1ij}$, $\gamma'_{2 j}$, $\gamma'_{3ij}$  that are not empty.
 By construction the concatenation of these elements is $\gamma_{tj}$, for $t\in[0..n]$.
@@
 We obtain:
-\begin{equation*}
+{\small\begin{equation*}
 \begin{split}
@@
 \mybigdotcup_{i=0}^{m_1}{\gamma'_{1ij}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{1k}}\dotcup
- {\gamma'_{2 j}}\subst{\bigotimes_{k=m_1}^{0}\Post\,'_{1k}}\,\dotcup\\
-& \mybigdotcup_{i=0}^{m_2}{\gamma'_{3ij}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}~\dotcup~
+ {\gamma'_{2 j}}\subst{\bigotimes_{k=m_1}^{0}\Post\,'_{1k}}\,\dotcup\, \mybigdotcup_{i=0}^{m_2}{\gamma'_{3ij}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}\\
+=&
 {\mybigdotcup_{t=0}^{n} {\gamma_{tj}}\subst{\bigotimes_{k=t-1}^{0} \Post_{k}}}   
@@
 \end{equation*}
-
-Concerning predicates, we also separate predicates on $P$ from predicates on $Q$, and from the equality on the action filling the hole:\\
+}
+
+Concerning predicates, we also separate predicates on $P$ from predicates on $Q$, and from the equality on the action filling the hole:
 %\begin{small}
@@
 \begin{align*}
-\Pred\,''&=\Big(\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\ &\qquad
-~\quad\bigwedge_{i=0}^{m_3}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\Big)\\
+\Pred\,''&=\Big(\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land%\\ &\qquad
+%~\quad
+\bigwedge_{i=0}^{m_3}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\Post\,'_{1j}}\Big)\\
 &=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}\land\Pred_2\subst{\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\Big)\\&\qquad

### 2020-05-12 2016-Weak-FH-Bisim/WeakBisim.tex
state variables and positioning wrt forte

@@
 
-\ERIC{imported from FORTE'16, but many of these works also had weak
-  version... we need to have another look}
-
 In the nineties, several 
@@
 
-\paragraph{Previous Works and Contribution}
+\subsubsection*{Previous Works and Contribution}
 While most of our previous works relied on closed, fully-instantiated semantics~\cite{BBCHM:article2008,AmeurBoulifa2017,HKM-FASE16}, it is only recently that we could design a first version of a  parameterised semantics for pNets with a strong bisimulation equivalence~\cite{henrio:Forte2016}.
-This article builds open this previous parameterised semantics and provide a cleaner version of the semantics with a slightly simplified formalism and extends it to deal with weak bisimulation.
+This article builds open this previous parameterised semantics and provide a cleaner version of the semantics with a slightly simplified formalism, adding a notion of global state to automata.
 The slight simplification of the formula allowed us to adopt a much cleaner presentation where the theory for open automata, the algebra used to define the semantics of pNets with holes, can be studied independently from its application to pNets.
-Also, in previous work the study of compositionability was only partial, and in particular the proof that bisimulation is an equivalence is one new contribution of this article and provides a particularly interesting insight on the semantic model we use.
+Also, in \cite{henrio:Forte2016} the study of compositionability was only partial, and in particular the proof that bisimulation is an equivalence is one new contribution of this article and provides a particularly interesting insight on the semantic model we use.
 The new formalism allowed us to extend the work and define weak bisimulation  for open automata, which is entirely new.
@@
 
-\paragraph{Structure}
+\subsubsection*{Structure}
 This article is organised as follows. Section~\ref{sec:notations}
@@
 This section introduces the notations we will use in this article, and  recalls the definition of pNets~\cite{henrio:Forte2016} with an informal semantics  of the pNet constructs.
-In general $x_i,y_i$ range over variables.
-
-\TODO{Ludo: add positioning wrt FORTE (variables)}
+The only significant difference compared to our previous definitions is that we remove here the restriction that was stating that variables should be local to a state of a labelled transition system.
 
 \subsection{Notations}
+%In general $x_i,y_i$ range over variables.
 \subsubsection*{Term algebra.}
@@
 
-We distinguish two kinds of parameterised actions: one that distinguishes input variables and one that does not. Let $a$
-range over action labels, $\symb{op}$ be operators, and $x_i$ range over
+Let $a$
+range over action labels, $\symb{op}$ be operators, and $x_i$ and $y_i$ range over
 variable names.
 
+We distinguish two kinds of parameterised actions: one that distinguishes input variables and one that does not. 
 We first define the set of actions that distinguish input variables, they will be used in the definition of \pLTS\ below:
@@
 Note that we make no assumption on finiteness of the set of states nor
-on finite branching of the transition relation.
+on finite branching of the transition relation. Compared to our previous works~\cite{henrio:Forte2016,AmeurBoulifa2017} we extend the expressiveness of the model by making variables global.
 
@@
 
-\TODO{Ludo: add positioning wrt FORTE (variables)}
-
 The semantics of open pNets will be defined  as an open automaton. An open
@@
 action of some holes, the transition occurs if some predicates hold, and can involve a 
-set of state modifications. This section defines open automata and a bisimulation theory for them.
+set of state modifications.
+This section defines open automata and a bisimulation theory for them.
+This section can be viewed as an improved version of the formalism described in \cite{henrio:Forte2016}, generalising the automata with a notion of global variable, which makes the state of the automaton more explicit.
+We also adopt a semantics and logical interpretation of the automata that intuitively can be stated as follows: ``if a transition belongs to an open automaton, any refinement of this transition also belongs to the automaton''.
 
@@
 %\end{small}
-
 \begin{footnotesize}

### 2020-05-12 2016-Weak-FH-Bisim/WeakBisim.tex
improvement big proof arund page 57

@@
 				{\Post\,''_2}}
-			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_2}
+			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_{20}}
 				\ostate{t_l'^{\,l\in L_Q}}}
@@
 $\begin{array}{l}\displaystyle{
-\Pred_\beta=\bigwedge_{p=0}^{m_1}(\beta_{1pj_0}=\alpha_{1p})\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}} \wedge (\beta_{2j_0}=\alpha_2)\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}} \wedge \\\qquad\qquad
+\Pred_\beta=\bigwedge_{p=0}^{m_1}(\beta_{1pj_0}=\alpha_{1p})\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}} \wedge (\beta_{2j_0}=\alpha_{20})\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}} \wedge \\\qquad\qquad
 \displaystyle{
@@
 				{{\Post\,''_p}}}
-				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
+				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha'_{p}}
 				\ostate{v_{(p+1)l}^{l\in L_Q}}}
@@
 $\\ 
-In this equation, and using case 1 above for all $k\in [0\ldots n_1]$ there is a $p\in [0..m_1]$ such that $\alpha_{1p}=\alpha_k$ (following the re-indexing done in the removal of steps where $Q$ does not move), we know that $\Pred_{1p}$ contains the predicate $( \alpha_{1p}=\beta_{1 p j_0})$.
-Because $\beta_{1 p j_0}$ only contains variables of $P$ and $\alpha_k$ only variables of $Q$, we have:
+In this equation, and using case 1 above for all $k\in [0\ldots n_1]$ there is a $p\in [0..m_1]$ such that $\alpha_{1p}=\alpha'_k$ (following the re-indexing done in the removal of steps where $Q$ does not move), we know that $\Pred_{1p}$ contains the predicate $( \alpha_{1p}=\beta_{1 p j_0})$.
+Because $\beta_{1 p j_0}$ only contains variables of $P$ and $\alpha'_k$ only variables of $Q$, we have:
 \begin{equation*}
@@
 = \beta_{1 p j_0}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,'_{1j}} \\
-&\iff\alpha_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post\,''_{j}}= \beta_{1 p j_0}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,'_{1j}} 
+&\iff\alpha'_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post\,''_{j}}= \beta_{1 p j_0}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,'_{1j}} 
 \end{split}
 \end{equation*}
-We can obtain similar equations for $\alpha_{n_1+1}$ related with $\beta_{2 j_0}$ and the  $\alpha_k$ for $k\geq n_1+2$ related with $\beta_{3 p j_0}$ for some $p$.
+We can obtain similar equations for $\alpha'_{n_1+1}$ related with $\beta_{2 j_0}$ and the  $\alpha'_k$ for $k\geq n_1+2$ related with $\beta_{3 p j_0}$ for some $p$.
 Note that the substitutions are however more complex in the other cases.
@@
 \Pred_\beta \iff \gamma_{j_0}=
-\vis{[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,''_{j}}|p\in[0..n_1+n_2+2]]}
+\vis{[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,''_{j}}|p\in[0..n_1+n_2+2]]}
 \end{equation}
@@
 
-Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha_p$ some of them may be non-observable (they are $\tau$ transitions).
-By considering the sequence of $\tau$ and non-$\tau$ actions we split the sequence of actions into $n+1$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action, and possibly many non-observable ($\tau$) ones.
+Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha'_p$ some of them may be non-observable (they are $\tau$ transitions).
+By considering the sequence of $\tau$ and non-$\tau$ actions we split the sequence of actions into $n+1$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action that will be named $\alpha_p$, and possibly many non-observable ($\tau$) ones.
 
@@
 				{{\Post\,''_{n_k}}}}
-				{\ostate{v_{n_kl}^{l\in L_Q}} \OTarrow {\alpha_{{n_k}}}
+				{\ostate{v_{n_kl}^{l\in L_Q}} \OTarrow {\alpha'_{{n_k}}}
 				\ostate{v_{(n_k+1)l}^{l\in L_Q}}}
@@
 				{{\Post_k}}}
-			{\ostate{v_{kl}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
+			{\ostate{v_{kl}^{l\in L_Q}} \OTWeakarrow {\alpha_{k}}
 				\ostate{(v_{kl}')^{l\in L_Q}}}
@@
 \forall l \in L_Q. &v_{kl}=v_{(n'_{k})l} \wedge v_{kl}'=v_{(n'_k)l}\\
-\alpha_k'=&\alpha_{n_k}{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}}\\
+\alpha_k=&\alpha'_{n_k}{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}}\\
 {\gamma_{kj}^{j\in J\cap\Holes(Q)} }=&{\mybigdotcup_{i=n'_{k}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}} \dotcup\\
@@
 Consequently,  we have:
-\[\alpha_{n_k}\displaystyle{\subst{\!\bigotimes_{j=n_k-1}^{0}\!\!\!\Post\,''_{j}}} =
-\alpha_{n_k}\displaystyle{\subst{\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post''_{j}\otimes\!\!\!\bigotimes_{j=n'_{k}-1}^{0}\!\!\!\Post\,''_{j}}} = \alpha_k'\displaystyle{\subst{\!\bigotimes_{j=n'_{k}-1}^{0}\!\!\!\Post\,''_{j}}} =
-\alpha_k'\displaystyle{\subst{\!\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}}\]
-With~\ref{eqproofbeta}, we now have (the actions $\alpha'_p$ correspond to the observable actions, $\alpha_k$): 
+\[\alpha'_{n_k}{\subst{\!\bigotimes_{j=n_k-1}^{0}\!\!\!\Post\,''_{j}}} =
+\alpha'_{n_k}\displaystyle{\subst{\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post''_{j}\otimes\!\!\!\bigotimes_{j=n'_{k}-1}^{0}\!\!\!\Post\,''_{j}}} = \alpha_k\displaystyle{\subst{\!\bigotimes_{j=n'_{k}-1}^{0}\!\!\!\Post\,''_{j}}} =
+\alpha_k\displaystyle{\subst{\!\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}}\]
+With~\ref{eqproofbeta}, we now have. Recall that the actions $\alpha_k$ are the actions $\alpha'_{p}$ that are observable: 
 \begin{eqnarray*}
@@
 \mybigdotcup_{p=0}^{p=n_1+n_2+2}
-\vis{\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}}\\
+\vis{\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}}\\
 %&\iff&\gamma_{j_0}=
@@
 &\iff& \gamma_{j_0}=
-[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n]]
+[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n]]
 \end{eqnarray*}
@@
 \[\Pred = \displaystyle{\Pred\,'
-		\land \!\!\bigwedge_{p=0}^n((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} )}\]
+		\land \!\!\bigwedge_{p=0}^n\Big((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i}) = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i}) \Big)}\]
 Indeed,
@@
 &\qquad\land\left(\Pred\,'_{2}
-		\land {\Pred\,''_{2}}\land \alpha_{2}=\beta_{2j_0}\right)\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
+		\land {\Pred\,''_{2}}\land \alpha_{20}=\beta_{2j_0}\right)\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
 &\qquad\land\bigwedge_{i=0}^{m_2} \left(\Pred\,'_{3i}
@@
 &\qquad\land \left(\Pred\,'_{2}\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}
-		\land {\Pred\,''_{2}} \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \land (\alpha_{2}=\beta_{2j_0})\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \right) \\
+		\land {\Pred\,''_{2}} \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \land (\alpha_{20}=\beta_{2j_0})\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \right) \\
 &\qquad\land\bigwedge_{i=0}^{m_2} \Bigg(\Pred\,'_{3i} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} 
@@
 \\&\iff \Pred\,'\land\bigwedge_{k=0}^n\Pred_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}\land
-(\gamma_{j_0}=[\alpha'_{i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{j}}|i\in[0..n]])
+(\gamma_{j_0}=[\alpha_{i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{j}}|i\in[0..n]])
 \end{align*}
 \end{scriptsize}
-which is exactly what is needed.
+which is exactly what is needed with $\gamma_{j_0}=[\beta_0..\beta_n]$.
 
@@
 &=\bigotimes_{j=m_2}^{0}\!\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j} \uplus \bigotimes_{j=m_2}^{0}\!\!\Post\,''_{3j}\shortotimes\Post\,''_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,''_{1j}\\
-&=\Post\,' \uplus \bigotimes_{j=n'_{n+1}-1}^{0}\!\!\Post\,''_{j}\qedhere
+&=\Post\,' \uplus \bigotimes_{j=n'_{n+1}-1}^{0}\!\!\Post\,''_{j}
 \end{align*}}
+Which concludes because we have we have $\displaystyle{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post\,''_{j} = \bigotimes_{j=k-1}^{0}\!\!\Post_{j}}$.
 %

### 2020-05-19 2016-Weak-FH-Bisim/WeakBisim.tex
small edits before pulling...

--- 2020-05-12 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
-\TODO{Ludo: add positioning wrt FORTE (variables)}
-
 \subsection{Notations}
@@
 
+\paragraph{Proving bisimulation in practice}
+
 \subsection{Weak bisimulation for open pNets}
@@
 developed algorithms to check strong FH-bisimulation \cite{hou:hal-02406098}.  
-
-\ERIC{
-  =>  Expliquer deux versions algos bisim (check/on-the-fly)\\
-=> Do we need comment on Simplification ? I'm not sure I can write
-something definitive, and Zechen is currently working on it.\\
-=> idees pour implementer Weak efficacement (= sans construire WOA) ?}
-
-\TODO{Further work: Branching ? Refinements ? }
+Naturally we are now working toward an implementation of weak FH-Bisimulation. 
+The challenges here, in the context of uour symbolic systems, is not so much algorithmic complexity,
+as was the case with classical weak bisimulation on finite models, but decidability and termination.
+Two main directions should be explored, either with an explicite construction of the weak transition, but this step in
+itself may introduce non-termination, or a direct implementation of the weak bisimulation definition, without
+constructing the weak automaton. We can expect that optimisations here in the symbolic setting would be quite different from the classical case.
 
@@
 This concludes the inductive step, showing  that the decomposition expressed by the $\Leftarrow$ direction of the lemma is always possible with the right side conditions. 
-\qedhere
 \end{itemize}
@@
 With:
-{\small
-\begin{align*}
-\forall l \in L_Q. &v_{kl}=v_{(n'_{k})l} \wedge v_{kl}'=v_{(n'_k)l}\\
-\alpha_k'=&\alpha_{n_k}{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}}\\
-{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=&{\mybigdotcup_{i=n'_{k}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}} \dotcup\\
-&\mybigdotcup_{i=n_k+1}^{n'_{k+1}-1}
+$\forall l \in L_Q. v_{kl}=v_{(n'_{k})l} \wedge v_{kl}'=v_{(n'_k)l}$\\
+$\alpha_k'=\alpha_{n_k}\displaystyle{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}}$\\
+$\displaystyle{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=\displaystyle{\mybigdotcup_{i=n'_{k}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}} \dotcup\\
+{}~~\qquad \qquad\qquad\mybigdotcup_{i=n_k+1}^{n'_{k+1}-1}
 \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}} \subst{\bigotimes_{l=i-1}^{n_k\!+\!1}\!\Post\,''_{l}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}} }\\
-\Pred_k=&\bigwedge_{i=n'_{k}}^{n_k\!-\!1}\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\Pred\,''_{n_k} \subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\\ 
-&\bigwedge_{i=n_k+1}^{n'_{k+1}-1}\!\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\!\Post\,''_{j}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{j}}
+%
+\Pred_k=\bigwedge_{i=n'_{k}}^{n_k\!-\!1}\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\Pred\,''_{n_k} \subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\\ 
+{}~\qquad\quad\bigwedge_{i=n_k+1}^{n'_{k+1}-1}\!\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\!\Post\,''_{j}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{j}}
 \\
-\Post_k= &\bigotimes_{j=n'_{k+1}-1}^{n'_{k}}\!\!\Post\,''_{j}
-\end{align*}
-}
+\Post_k= \bigotimes_{j=n'_{k+1}-1}^{n'_{k}}\!\!\Post\,''_{j}$\\
 
@@
 
-We need now to show that the set of WOT obtained above verifies the conditions of the lemma, i.e. it is a set of WOT of the form:
+We need now to show that this set of WOT verifies the conditions of the lemma, i.e. it is a set of WOT of the form:
 \[	Q\models{\openrule
@@
 Overall, we have
-$\forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i$ (see above):\\
+$\forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i$ (see above)\\
 {\scriptsize \begin{equation*}
@@
 }
-Next, we have
-\[\Pred = \displaystyle{\Pred\,'
-		\land \!\!\bigwedge_{p=0}^n((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} )}\]
+$\Pred = \displaystyle{\Pred\,'
+		\land \!\!\bigwedge_{p=0}^n((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i)} )}$\\
 Indeed,
-\begin{scriptsize}
-\begin{align*}
+\begin{small}
+\begin{equation*}
+\begin{split}
 \Pred&\iff\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\land
@@
 &\qquad\land\bigwedge_{i=0}^{m_2} \left(\Pred\,'_{3i}
-		\land {\Pred\,''_{3i}}\land \alpha_{3i}=\beta_{3ij_0}\right) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\displaybreak[0]\\
+		\land {\Pred\,''_{3i}}\land \alpha_{3i}=\beta_{3ij_0}\right) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
 &\iff\bigwedge_{i=0}^{m_1}\left((\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{1j}})
@@
 (\gamma_{j_0}=[\alpha'_{i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{j}}|i\in[0..n]])
-\end{align*}
-\end{scriptsize}
-which is exactly what is needed.
-
+\end{split}\end{equation*}
+\end{small}
+which is exactly what is needed.\\
 Finally we have~~
@@
 because
-{\small \begin{align*}
+\begin{equation*}
+\begin{split}
 \Post&=\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}\\
 &=\bigotimes_{j=m_2}^{0}\!\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j} \uplus \bigotimes_{j=m_2}^{0}\!\!\Post\,''_{3j}\shortotimes\Post\,''_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,''_{1j}\\
-&=\Post\,' \uplus \bigotimes_{j=n'_{n+1}-1}^{0}\!\!\Post\,''_{j}\qedhere
-\end{align*}}
+&=\Post\,' \uplus \bigotimes_{j=n'_{n+1}-1}^{0}\!\!\Post\,''_{j}
+\end{split}
+\end{equation*}
 %
@@
 \end{mathpar}
-Let 
+Let\\[-3ex] 
+\begin{mathpar}
 %J_Q=\displaystyle{\bigcup_{t=0}^nJ_{t}}
-\qquad
-$\Pred\,'=\Pred\land (\beta_{j_0}=\alpha_Q\land \Pred_Q) \quad\text{~~and~~}\quad
+%\qquad
+\Pred\,'=\Pred\land (\beta_{j_0}=\alpha_Q\land \Pred_Q) \quad\text{~~and~~}\quad
 %\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
 \Post\,'=\Post\uplus\Post_Q
-$
-
-Then, we have
-{\small	\[ P[Q]_{j_0}  
+\end{mathpar}
+Then, we have\\[-3ex]
+	\[ P[Q]_{j_0}  
 	\models
@@
 	}
-	\]}
+	\]
 \end{lemma}
 \begin{proof}
-By  Lemma \ref{lem-rel-OT-WOT} we can decompose the WOT of $Q$ into  a series of $k+1$ and $k'+1$ tau open transitions and an $\alpha'_Q$ open transition (that can be observable or not depending on $\alpha_Q$):
+By  Lemma \ref{lem-rel-OT-WOT} we can decompose the WOT of $Q$ into  a series of $k+1$ and $k'+1$ tau open transitions and an observable open transition:
 \begin{mathpar}
@@
 
-\item For the possibly observable open transition.  By Lemma \ref{lem-compose} with the lemma hypotheses we obtain:\\ 
+\item For the observable open transition.  By Lemma \ref{lem-compose} with the lemma hypotheses we obtain:\\ 
 	\[ P[Q]_{j_0}  
@@
 $\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$
-and $\alpha=\alpha'$  because $\Post_{1j}$ acts on variables of $Q$ and $\alpha$ contains only variables of $P$.
+and $\alpha=\alpha'$  because $\Post_{1j}$ acts on variables of $Q$ and $\alpha$ contains only variables of $P$.\\
+$\displaystyle{
+\set{\gamma_c}=\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{i=h-1}^{0}\!\!
+\Post_{1i} } }  \dotcup  \vis{({\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2})\subst{\bigotimes_{i=k}^{0}\Post_{1i}}} \dotcup}$ \\
+${}~~\hspace{1.8em}\displaystyle{\mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{i=h-1}^{0}\!\!\Post_{3i}\shortotimes\Post_2\shortotimes\bigotimes_{i=k}^{0}\Post_{1i}} }}$\\
+${}~~\hspace{0.6em}=\set{\gamma}\uplus\vis{\beta_j^{\in J\setminus \{j_0\}}} \quad$  because $\Post_{1j}$  does not act on variables of $\beta_j$.  \\
 \begin{small}
-\begin{align*}
-\set{\gamma_c}=&\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{i=h-1}^{0}\!\!
-\Post_{1i} } }  \dotcup  \vis{({\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2})\subst{\bigotimes_{i=k}^{0}\Post_{1i}}} \dotcup\\
-&\mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{i=h-1}^{0}\!\!\Post_{3i}\shortotimes\Post_2\shortotimes\bigotimes_{i=k}^{0}\Post_{1i}} }\\
-=&\set{\gamma}\uplus\vis{\beta_j^{\in J\setminus \{j_0\}}} \quad  \text{ because $\Post_{1j}$  does not act on variables of $\beta_j$.}  
-\displaybreak[0]\\
-\Pred_c=&
-\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_{1i}}\land
-\left(Pred\land\Pred_2\land \alpha'_Q=\beta_{j_0}\right) \subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land\\
-&\bigwedge_{h=0}^{k'}{\Pred_{3h}}\subst{\bigotimes_{i=h-1}^{0}{\Post_{3i}}\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}
-\\
-\Post_c=&(\bigotimes_{i=k'}^{0}{\Post_{3i}})\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}
-\end{align*}
+$\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_{1i}}\land
+\left(Pred\land\Pred_2\land \alpha'_Q=\beta_{j_0 }\right)\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land\\\displaystyle
+\bigwedge_{h=0}^{k'}{\Pred_{3h}}\subst{\bigotimes_{i=h-1}^{0}{\Post_{3i}}\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}
+\end{array}
+$\\
+$\Post_c=\displaystyle{(\bigotimes_{i=k'}^{0}{\Post_{3i}})\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}$
 \end{small}
+
 \noindent Note that we have $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$.
 
-Note also that $\Post$ only acts on variables of $P$ while $\Post_{1i}$ only acts on  variables of $Q$.
+Note also that $\Post$ only acts on variables of $P$ while $\Post_{1i}$ only acts on state variables of $Q$.
 We conclude on predicate and posts as follows\footnote{$\Post_{1i}$ only has an effect on variables of $Q$ and thus does not modify $\Pred$ or $\beta_{j_0}$}:
@@
 &=\Pred_Q\land\Pred\land \alpha_Q=\beta_{j_0}\\[.3ex]
-\Post_c&=\Post\uplus\Post_Q \qedhere
+\Post_c&=\Post\uplus\Post_Q \\[-3ex]
 \end{split}
@@
 \end{proof}
-\smallskip
+
 \begin{lemma}[Weak open transition composition]\label{lem-Weakcompose} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
@@
 		\ostate{s_i'^{\, i\in L}}}
-}
-\qquad\text{~~and for all $p\in[0..n]$~~}\quad
+}\\
+\text{~~and for all $p\in[0..n]$~~}
 Q\models{\openrule
@@
 J_Q=\displaystyle{\bigcup_{p=0}^nJ_{p}}
-
-\forall{i\in L_Q}.\,s_i=s_{0i}~~\land~~s'_i=s_{(n+1) i}
-
-\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}\subst{\bigotimes_{k=p}^{0}{\Post_k}}}
-
+\qquad
 \Pred\,'=\Pred\land \bigwedge_{p=0}^{n}(\alpha_t=\beta_t\land \Pred_t)\bigotimes_{i=p-1}^{0}\Post_i
-
+\\
+\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}\subst{\bigotimes_{k=p}^{0}{\Post_k}}}\text{\quad and\quad}
 \Post\,'=\Post\uplus\bigotimes_{p=n}^{0}
 		\Post_p
-\end{mathpar}
-Then, we have
+\\
+\forall{i\in L_Q}.\,s_i=s_{0i} \text{\quad and \quad} \forall {i\in L_Q}.\,s'_i=s_{(n+1) i}
+\end{mathpar}
+Then, we have\\[-2ex]
 	\[ P[Q]_{j_0}  
@@
 \begin{small}
-$\forall p\!\in\![0\,..\,m_1].P\models\openrule
+$\forall p\!\in\![0..m_1].P\models\openrule
     {{\beta_{1pj}^{j\in J_{1p}}},\Pred_{1p},\Post_{1p}   }
@@
 \\
-and  $\forall p \in [0\,..\,m_2].P\models\openrule
+and  $\forall p \in [0..m_2].P\models\openrule
          {
@@
 \end{small}
+~~\\
 %\end{mathpar}
-
- where:
-{\small\begin{align*}
-\forall i\in L.~~s_i=s_{10 i} &\wedge s_{1(m_1+1) i}=s_{20i} \wedge  s_{21i}= s_{30 i} \wedge s_{3(m_2+1) i}=s'_i\\
-\alpha=&\alpha'{\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \\
-\gamma_j^{j\in J}=&{\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \dotcup \, \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}}\, \dotcup\\
-&\mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{3p}} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}\\
-\Pred=&{\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\big)\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land}\\ 
-&{\bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}}\\
-\Post=&{\bigotimes_{p=m_2}^{0}\Post_{3p}\otimes\Post_2\otimes\bigotimes_{j=m_1}^{0}\Post_{1j}}
-\end{align*}
-}
+\noindent where for all $i\in L$:\\
+$s_i=s_{10 i} \wedge s_{1(m_1+1) i}=s_{20i} \wedge  s_{21i}= s_{30 i} \wedge s_{3(m_2+1) i}=s'_i$\\
+$\alpha=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}}$ \\
+%\begin{multline*}
+$\gamma_j^{j\in J}=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \dotcup \, \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}}\, \dotcup\\
+{}~\qquad\quad \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{3p}} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}$\\
+%\end{multline*}
+%\begin{multline*}
+$\Pred=\displaystyle{\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\big)\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land}$\\ 
+${}~~\qquad\quad\displaystyle{\bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}}$\\
+$\Post=\displaystyle{\bigotimes_{p=m_2}^{0}\Post_{3p}\otimes\Post_2\otimes\bigotimes_{j=m_1}^{0}\Post_{1j}}$\\
+%\end{multline*}
 
@@
 which the hole $j_0$ moves in the 3 sets of OTs above ($\beta_m$ is the action that matches the hole $j_0$ in the OT $\alpha'$), in other words, we have for all $i$, $\beta_{1 n_i j_0}$ a visible action, as additionally:\\
-{\small
-$\gamma_{j_0}=~[\beta_0..\beta_n]\\
-\mbox{~~}\quad =
-\displaystyle{\mybigdotcup_{\substack{i=0\\j_0\in J_{1i}}}^{m_1} \vis{{\beta_{1ij_0}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \,\dotcup\, \vis{{\beta_{2j_0}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}}\, \,\dotcup \\
-\mbox{~~~~}\qquad \displaystyle{ \mybigdotcup_{\substack{i=0\\j_0\in J_{3i}}}^{m_2} \vis{{\beta_{3ij_0}} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}}$}
+$\gamma_{j_0}=[\beta_0..\beta_n]\\
+\mbox{~~}\quad =\displaystyle{\mybigdotcup_{\substack{i=0\\j_0\in J_{1i}}}^{m_1} \vis{{\beta_{1ij_0}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \dotcup \vis{{\beta_{2j_0}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}}\, \dotcup \\
+\mbox{~~~~}\qquad\displaystyle{ \mybigdotcup_{\substack{i=0\\j_0\in J_{3i}}}^{m_2} \vis{{\beta_{3ij_0}} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}}$\\
 
 \noindent We have, by definition of $n_i$ and $n'_i$:\\
-$\displaystyle{\forall{i\in[0\,..\,m\!-\!1]}, \beta_{1 n_i j_0}\subst{\bigotimes_{k=n_i-1}^{0}\Post_{1k}}=\beta_i}$, \qquad$\displaystyle{\beta_{2 j_0}\subst{\bigotimes_{k=m_1}^{0} \Post_{1k} }=\beta_m}$, and \\
-$\displaystyle{\forall{i\in[m\!+\!1\,..\,n]}, \beta_{3 n_i' j_0}\subst{\bigotimes_{k=n_i'-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}=\beta_i}$\\
-
-\noindent Now, we compose OTs for each of the case above (depending on the OT of $P$):
+$\displaystyle{\forall{i\in[0..m-1]}, \beta_{1 n_i j_0}\subst{\bigotimes_{k=n_i-1}^{0}\Post_{1k}}=\beta_i}$, $\displaystyle{\beta_{2 j_0}\subst{\bigotimes_{k=m_1}^{0} \Post_{1k} }=\beta_m}$, and \\
+$\displaystyle{\forall{i\in[m+1..n]}, \beta_{3 n_i' j_0}\subst{\bigotimes_{k=n_i'-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}=\beta_i}$\\
+
+\noindent Now, we compose OTs for each of the case above (OTs of $P$):
 \begin{enumerate}
-\item For the first $\tau$ OTs, i.e, $p\in [0\,..\,m_1]$. We have: \\
+\item For the first $\tau$ OTs, i.e, $p\in [0..m_1]$. We have: \\
 Either there is $i$ such that $p=n_i$, and thus $\beta_i$ and $\beta_{1 p j_0}$ are defined. In this case by Lemma~\ref{lem-Weakcompose1},  we have: 
@@
 	\]
-with 
-\begin{mathpar}
- \set{\gamma'_{1p}}=\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{1pj}^{j\in J_{1p}\setminus \{j_0\}}}
-
-\Pred\,'_{1p}=\Pred_{1p}\land (\beta_{1pj_0}=\alpha_i\land \Pred_i)
-
- \Post\,'_{1p}=\Post_{1p}\uplus\Post_i
-\end{mathpar}
+with \\
+
+$ \set{\gamma'_{1p}}=\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{1pj}^{j\in J_{1p}\setminus \{j_0\}}},
+\Pred\,'_{1p}=\Pred_{1p}\land (\beta_{1pj_0}=\alpha_i\land \Pred_i)$, and\\
+
+$ \Post\,'_{1p}=\Post_{1p}\uplus\Post_i$\\
 
@@
          {	\set{\gamma'_2},\Pred\,'_2,\Post\,'_2 }
-         {\ostate{{(s_{20j})}^{j\in L}\uplus (s_{mj})^{j\in L_Q}}\OTWeakarrow {\alpha'} \ostate{{(s_{21j})}^{j\in L}\uplus (s_{(m+1)j})^{j\in L_Q}}}\]
-with
-\begin{mathpar}
-\set{\gamma'_2}=\gamma_{m j}^{j\in J_m}\uplus\vis{\beta_{2j}^{j\in J_2\setminus \{j_0\}}}
-
-\Pred\,'_{2}=\Pred_{2}\land (\beta_{2j_0}=\alpha_m\land \Pred_m)
-
-\Post\,'_{2}=\Post_{2}\uplus\Post_m
-\end{mathpar}
-
-\item For the last $\tau$ OTs, i.e, $p\in [0\,..\,m_2]$. We have similarly to the first case:\\
+         {\ostate{{s_{20j}}^{j\in L}\uplus s_{mj}^{j\in L_Q}}\OTWeakarrow {\alpha'} \ostate{{(s_{21j})}^{j\in L}\uplus s_{(m+1)j}^{j\in L_Q}}}\]
+with\\
+
+$\set{\gamma'_2}=\gamma_{m j}^{j\in J_m}\uplus\vis{\beta_{2j}^{j\in J_2\setminus \{j_0\}}},
+\Pred\,'_{2}=\Pred_{2}\land (\beta_{2j_0}=\alpha_m\land \Pred_m)$, and\\
+
+$\Post\,'_{2}=\Post_{2}\uplus\Post_m$\\
+
+\item For the last $\tau$ OTs, i.e, $p\in [0..m_2]$. We have similarly to the first case:\\
  Either there is $i$ such that $p=n'_i$, and thus $\beta_i$ and $\beta_{1 p j_0}$ are defined. In this case by Lemma~\ref{lem-Weakcompose1}, we have: 
@@
 	\]
-with
-\begin{mathpar}
-\set{\gamma'_{3p}}=\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{3pj}^{j\in J_{3p}\setminus \{j_0\}}}
-
+with\\
+
+$\set{\gamma'_{3p}}=\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{3pj}^{j\in J_{3p}\setminus \{j_0\}}}, 
 \Pred\,'_{3p}=\Pred_{3p}\land (\beta_{3pj_0}=\alpha_i\land \Pred_i)
-
-\Post\,'_{3p} =\Post_{3p}\uplus\Post_i
-\end{mathpar}
+$ and,\\
+
+$\Post\,'_{3p} =\Post_{3p}\uplus\Post_i$\\
 
@@
 	\]
-Where
-{\small 
-\begin{align*}
-\alpha''=&\alpha'{\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}\\
-\set{\gamma'}=&
+Where\\
+{\small $
+\alpha''=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}\\
+\displaystyle{
+\set{\gamma'}=
  \mybigdotcup_{i=0}^{m_1}\set{\gamma'_{1i}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{1k}}\,\dotcup\,
@@
  \mybigdotcup_{i=0}^{m_2}\set{\gamma'_{3i}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}
-\displaybreak[0]\\
-\Pred\,''=&\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\ 
-&\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_2}^{0}\Post\,'_{1j}}\displaybreak[0]\\
-\Post\,''=&\bigotimes_{j=m_2}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}
-\end{align*}
 }
+\\
+\Pred\,''=\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\ 
+{}~\qquad\qquad\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_2}^{0}\Post\,'_{1j}}\\
+\Post\,''=\bigotimes_{j=m_2}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}
+$
+}
 
 However it must be noticed that in steps 1 and 3, we have two kinds of WOTs with different signatures (depending on whether $Q$ moves or not).
-It is still possible to glue them together in a global rule with two more terms for $\Pred$ and $\Post$ terms.
+It is still possible to glue them together in a global rules with two more terms for $\Pred$ and $\Post$ terms.
 This global merge is possible because the post-conditions of $P$ only act on variables of $P$ and those of $Q$ on variables of $Q$ (for example $\Post_i$ has no effect on $\Pred_{1p}$ and thus does not need to be taken into account when dealing with WOTs where $Q$ does not move).
@@
 We now  compare each element of the obtained WOT with the conclusion of the lemma:
-{\small \begin{align*}
+\begin{align*}
 \alpha''&=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}}\\
@@
 & = \alpha
-\end{align*}}
+\end{align*}
 
 For $\set{\gamma'}$ we distinguish elements in the holes of $P$ and of $Q$.
-
 First suppose $j\in J\setminus\{j_0\}$ we have $\gamma'_j=\gamma_j$ because $\Post'_{ij}$ has no effect on variables of $P$ and on $\beta_{1pj}$, consequently\\
-{\small \begin{equation*}
-\begin{split}\gamma'_j=&\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}}\subst{\bigotimes_{k=i-1}^{0}\! \Post_{1k} } }  \dotcup  \vis{{\beta_{2j}}\subst{\bigotimes_{k=m_1}^{0}\!\Post_{1k}}}\, \dotcup
+\begin{equation*}
+\begin{split}\gamma'_j=&\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \dotcup  \vis{{\beta_{2j}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}\, \dotcup\\
+&
 \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}
@@
 \end{equation*}
-}
-
-Second, when $j\in J_t$ for some $t$,  $\gamma'_j$ is the concatenation of elements of $\gamma'_{1ij}$, $\gamma'_{2 j}$, $\gamma'_{3ij}$  that are not empty.
+
+Now, when $j\in J_t$ for some $t$,  $\gamma'_j$ is the concatenation of elements of $\gamma'_{1ij}$, $\gamma'_{2 j}$, $\gamma'_{3ij}$  that are not empty.
 By construction the concatenation of these elements is $\gamma_{tj}$, for $t\in[0..n]$.
@@
 We obtain:
-{\small\begin{equation*}
+\begin{equation*}
 \begin{split}
@@
 \mybigdotcup_{i=0}^{m_1}{\gamma'_{1ij}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{1k}}\dotcup
- {\gamma'_{2 j}}\subst{\bigotimes_{k=m_1}^{0}\Post\,'_{1k}}\,\dotcup\, \mybigdotcup_{i=0}^{m_2}{\gamma'_{3ij}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}\\
-=&
+ {\gamma'_{2 j}}\subst{\bigotimes_{k=m_1}^{0}\Post\,'_{1k}}\,\dotcup\\
+& \mybigdotcup_{i=0}^{m_2}{\gamma'_{3ij}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}~\dotcup~
 {\mybigdotcup_{t=0}^{n} {\gamma_{tj}}\subst{\bigotimes_{k=t-1}^{0} \Post_{k}}}   
@@
 \end{equation*}
-}
-
-Concerning predicates, we also separate predicates on $P$ from predicates on $Q$, and from the equality on the action filling the hole:
+
+Concerning predicates, we also separate predicates on $P$ from predicates on $Q$, and from the equality on the action filling the hole:\\
 %\begin{small}
@@
 \begin{footnotesize}
-\begin{align*}
-\Pred\,''&=\Big(\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land%\\ &\qquad
-%~\quad
-\bigwedge_{i=0}^{m_3}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\Post\,'_{1j}}\Big)\\
-&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}\land\Pred_2\subst{\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\Big)\\&\qquad
-\land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i%\\&\qquad
+\begin{equation*}
+\begin{split}
+\Pred\,''&=\Big(\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\ &\qquad
+~\quad\bigwedge_{i=0}^{m_3}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\Big)\\
+&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\
+&\qquad \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\Big)%\\&\qquad
+\land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i\\&\qquad
 \land \Big( \bigwedge_{i=0}^{m-1}(\beta_{1{n_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j={n_i}-1}^{0}\Post\,'_{1j}}\land(\beta_{2{j_0}}=\alpha_m) \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\ &\qquad
-~\quad\bigwedge_{i=m+1}^{n}(\beta_{3{n'_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j=n'_i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\Big)\displaybreak[0]\\
-&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}\big)\land\Pred_2\subst{\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\Big)\\&\qquad
-\land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i
+~\quad\bigwedge_{i=m+1}^{n}(\beta_{3{n'_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j=n'_i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\Big)\\
+&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\big)\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\&\qquad \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\Big)%\\&\qquad
+\land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i\\&\qquad
 \land \Big(\bigwedge_{i=0}^{m-1}(\beta_{i}=\alpha_i)\subst{\bigotimes_{j={i-1}}^{0}\Post_{j}}\land(\beta_m=\alpha_m )\subst{\bigotimes_{j=m}^{0}\Post_{j}}\land\\ &\qquad
@@
 &=\Pred
-\end{align*}
+\end{split}
+\end{equation*}
 \end{footnotesize}
@@
 
-\TODO{Check coherency, the use-case figures have been modified}
+\TODO{Je ne peux pas refaire tourner le code, il faut que je modifie le pNet Editor pour qu'ils n'utilise plus les variables d'etat... Donc les 3 prochaines pages sont obsoletes...}
 %% \TODO{keep ?}

### 2020-05-19 2016-Weak-FH-Bisim/WeakBisim.tex
corrections in the proofs

--- 2020-05-12 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 \begin{proof}
-By  Lemma \ref{lem-rel-OT-WOT} we can decompose the WOT of $Q$ into  a series of $k+1$ and $k'+1$ tau open transitions and an $\alpha'_Q$ open transition (that can be observable or not depending on $\alpha_Q$):
+By  Lemma \ref{lem-rel-OT-WOT} we can decompose the WOT of $Q$ into  a series of $k+1$ and $k'+1$ tau open transitions and an $\alpha'_Q$ open transition (observable or not depending on $\alpha_Q$):
 \begin{mathpar}
@@
  \mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{j=h-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=k}^{0}\Post_{1j}} }\\
-\Pred_Q=&\bigwedge_{h=0}^{k}\!\big(\Pred_{1h}\subst{\bigotimes_{j=h-1}^{0}\Post_j^1}\big)\land \Pred_2\subst{\bigotimes_{h=k}^{0}\Post_{1h}}\land\\
-&		\bigwedge_{h=0}^{k'}\!\Pred_{3h}\subst{\bigotimes_{j=h-1}^{0}{\Post_{3j}}\otimes{\Post_2}  \otimes\bigotimes_{h=k}^{0}\Post_{1h}}\\
-\Post_Q=&\bigotimes_{h=k'}^{0}\Post_{3h}\otimes\Post_2\otimes\bigotimes_{j=k}^{0}\Post_{1j}
+\Pred_Q=&\bigwedge_{h=0}^{k}\!\Pred_{1h}\subst{\!\bigotimes_{j=h-1}^{0}\!\!\!\Post_{1 j}}\land \Pred_2\subst{\bigotimes_{h=k}^{0}\!\Post_{1h}}\land%\\
+%&
+	\!\bigwedge_{h=0}^{k'}\!\Pred_{3h}\subst{\!\! 	\bigotimes_{j=h-1}^{0}\!\!\!{\Post_{3j}}\otimes{\Post_2}  \otimes\bigotimes_{h=k}^{0}\!\!\Post_{1h}}\\
+\Post_Q=&\bigotimes_{h=k'}^{0}\!\!\Post_{3h}\otimes\Post_2\otimes\bigotimes_{j=k}^{0}\!\!\Post_{1j}
 \end{align*}
@@
 
-\Pred\,'=\Pred\land \bigwedge_{p=0}^{n}(\alpha_t=\beta_t\land \Pred_t)\bigotimes_{i=p-1}^{0}\Post_i
+\Pred\,'=\Pred\land \bigwedge_{p=0}^{n}(\alpha_p=\beta_p\land \Pred_p)\subst{\bigotimes_{i=p-1}^{0}\Post_i}
 
@@
 \end{lemma}
-~~\\
+
 \begin{proof} Suppose we have:
@@
  where:
-{\small\begin{align*}
-\forall i\in L.~~s_i=s_{10 i} &\wedge s_{1(m_1+1) i}=s_{20i} \wedge  s_{21i}= s_{30 i} \wedge s_{3(m_2+1) i}=s'_i\\
+{\small
+\begin{align*}
+\forall i\in L.&~~s_i=s_{10 i} \wedge s_{1(m_1+1) i}=s_{20i} \wedge  s_{21i}= s_{30 i} \wedge s_{3(m_2+1) i}=s'_i\\
 \alpha=&\alpha'{\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \\
-\gamma_j^{j\in J}=&{\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \dotcup \, \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}}\, \dotcup\\
+\gamma_j^{j\in J}=&{\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigotimes_{k=i-1}^{0}\!\!
+\Post_{1k} } }  \dotcup \, \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}}\, \dotcup\\
 &\mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{3p}} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}\\
-\Pred=&{\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\big)\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land}\\ 
-&{\bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}}\\
+\Pred=&{\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\subst{\!\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}\big)\land\Pred_2\subst{\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\land}%\\ 
+%&
+{\bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\bigotimes_{j=p-1}^{0}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}}\\
 \Post=&{\bigotimes_{p=m_2}^{0}\Post_{3p}\otimes\Post_2\otimes\bigotimes_{j=m_1}^{0}\Post_{1j}}
@@
 {\small
-$\gamma_{j_0}=~[\beta_0..\beta_n]\\
-\mbox{~~}\quad =
-\displaystyle{\mybigdotcup_{\substack{i=0\\j_0\in J_{1i}}}^{m_1} \vis{{\beta_{1ij_0}}\subst{\bigotimes_{k=i-1}^{0} \Post_{1k} } }  \,\dotcup\, \vis{{\beta_{2j_0}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}}\, \,\dotcup \\
-\mbox{~~~~}\qquad \displaystyle{ \mybigdotcup_{\substack{i=0\\j_0\in J_{3i}}}^{m_2} \vis{{\beta_{3ij_0}} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}}$}
+\begin{align*}
+\gamma_{j_0}=&~[\beta_0..\beta_n]\\
+ =&\!\!
+{\mybigdotcup_{\substack{i=0\\j_0\in J_{1i}}}^{m_1}\!\!\!
+\vis{{\beta_{1ij_0}}\subst{\!\bigotimes_{k=i-1}^{0} \!\!\!\Post_{1k} } }  \,\dotcup\, \vis{{\beta_{2j_0}}\subst{\!\bigotimes_{k=m_1}^{0}\!\!\Post_{1k}}}}\dotcup %\\
+%&
+{ \!\mybigdotcup_{\substack{i=0\\j_0\in J_{3i}}}^{m_2}\!\! \vis{{\beta_{3ij_0}} \subst{\!\bigotimes_{k=i-1}^{0}\!\!\!\Post_{3k}\shortotimes\Post_2\shortotimes
+\!\bigotimes_{k=m_1}^{0}\!\!\Post_{1k}}}}
+\end{align*}}
 
@@
 
- First suppose $j\in J\setminus\{j_0\}$ we have $\gamma'_j=\gamma_j$ because $\Post'_{ij}$ has no effect on variables of $P$ and on $\beta_{1pj}$, consequently\\
+ First suppose $j\in J\setminus\{j_0\}$ we have $\gamma'_j=\gamma_j$ because $\Post^{\,\prime}_{ij}$ has no effect on variables of $P$ and on $\beta_{1pj}$, consequently\\
 {\small \begin{equation*}
@@
 \[\forall x.\, (S'_Q,S'_{Q' x}| \Pred_{Q,Q' x})\in\mathcal{R}_{Q,Q'}\]
+
 and
-\begin{equation*}
-\begin{split}
-\Pred_{Q,Q'}\land \Pred_Q \implies &
-\Big(\bigvee_{x\in X}
-(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x})\Rightarrow (\Pred_{Q_x}\land\\ &~~\alpha_Q=\alpha_x \land \Pred_{Q,Q' x}\subst{\Post_{Q' x}\uplus \Post_{Q}}) \Big)
-\end{split}
-\end{equation*}
+{\small%\begin{equation*}
+\begin{multline*}
+\Pred_{Q,Q'}\land \Pred_Q \implies \\
+\bigvee_{x\in X}
+(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x})\Rightarrow (\Pred_{Q_x}\land%\\ %&~~
+\alpha_Q=\alpha_x \land \Pred_{Q,Q' x}\subst{\Post_{Q' x}\uplus \Post_{Q}}) 
+\end{multline*}
+%\end{equation*}
+}
 
@@
 with $\displaystyle{\bigvee_{x\in X}
-(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x} \implies \alpha_Q=\alpha_x}$ that ensures that the open transitions can be recomposed when the OT fires.
+\big(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x} \implies \alpha_Q=\alpha_x\big)}$ that ensures that the open transitions can be recomposed when the OT fires.
 
@@
 \[\forall x.\, (S'_P\uplus S'_Q,S'_P\uplus S'_{Q' x}| \Pred_{Q,Q' x})\in\mathcal{R}\]
-which is trivially verified, and
-\begin{equation*}
-\begin{split}
-\Pred_{Q,Q'}\land \Pred_P\land \Pred_Q \implies &
+which is true, and
+\begin{multline*}
+\Pred_{Q,Q'}\land \Pred_P\land \Pred_Q \implies \\
 \Big(\bigvee_{x\in X}
-(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x}\land \forall j\in J_P.\, \vis{\beta_j}=\vis{\beta_j}))\Rightarrow\\
-& (\Pred_P\land \Pred_{Q' x}\land\\ &\quad\alpha=\alpha \land \Pred_{Q,Q' x}\subst{\Post_P\uplus\Post_{Q' x}\uplus \Post_{Q}}) \Big)
-\end{split}
-\end{equation*}
+(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x}\land \forall j\in J_P.\, \vis{\beta_j}=\vis{\beta_j}))\Rightarrow \\(\Pred_P\land \Pred_{Q' x}\land \alpha=\alpha \land \Pred_{Q,Q' x}\subst{\Post_P\uplus\Post_{Q' x}\uplus \Post_{Q}}) \Big)
+\end{multline*}
 We conclude by observing that $\Post_P$ has no effect on variables of $Q$ and $Q'$, and thus on $\Pred_{Q,Q' x}$
@@
 		\beta_j^{j\in( J_P\uplus J_Q)}, 
-		\Pred_P\land \Pred_Q,  
+		\Pred_P\land \Pred_Q \land \Pred,  
 		\Post_P\uplus \Post_Q}
@@
 \end{mathpar}
+
+With $\Pred \iff \alpha_Q=\beta_{j_0}$
 
@@
 \Big(\bigvee_{x\in X}
-(\forall j\in J_P.\, \vis{\beta_j}=\gamma_{j x} \land \vis{\alpha_Q}=\gamma_{j_0})\Rightarrow (\Pred_{Q_x}\land\\ &~~\alpha=\alpha_x \land \Pred_{P,P' x}\subst{\Post_{P' x}\uplus \Post_{P}}) \Big)
+(\forall j\in J_P.\, \vis{\beta_j}=\gamma_{j x} \land \vis{\alpha_Q}=\gamma_{j_0})\Rightarrow (\Pred_{P'_x}\land\\ &~~\alpha=\alpha_x \land \Pred_{P,P' x}\subst{\Post_{P' x}\uplus \Post_{P}}) \Big)
 \end{split}
@@
 This is just a particular case of the theorem but where notations get simplified because the inner pnet does a single transition.
- This way we can compose the WOTs of $P'$ with the OT of $Q$ and obtain, whenever $\vis{\beta_j}=\gamma_{j x} $:
+ This way we can compose the WOTs of $P'$ with the OT of $Q$ and obtain, with $\gamma_{j_0}=[\beta] $:
 \[
@@
 	{
-		\vis{\beta_j^{j\in J_Q}}\uplus\gamma_{j x}^{j\in J_Q}, 
-		\Pred_{P' x}\land \Pred_Q,  
+		\vis{\beta_j^{j\in J_Q}}\uplus\gamma_{j x}^{j\in J_P}, 
+		\Pred_{P' x}\land \Pred_Q \land \alpha_Q=\beta,  
 		\Post_{P' x}\uplus \Post_Q}
@@
 \[\forall x.\, (S'_P\uplus S'_Q,S'_{P' x}\uplus S'_Q, \Pred_{P,P' x})\in\mathcal{R}\]
-which is trivially verified, and
-\begin{equation*}
-\begin{split}
-\Pred_{P,P'}\land \Pred_P\land \Pred_Q \implies &
+which is true, and
+\begin{multline*}
+\Pred_{P,P'}\land \Pred_P\land \Pred_Q \Pred \implies \\
 \Big(\bigvee_{x\in X}
-(\forall j\in J_P.\, \vis{\beta_j}\gamma_{j x} \land \forall j\in J_Q.\, \vis{\beta_j}=\vis{\beta_j} )\Rightarrow\\
-& (\Pred_{P' x}\land \Pred_Q\land\\ &\quad\alpha_x=\alpha \land \Pred_{P,P' x}\subst{\Post_{P' x}\uplus\Post_P\uplus \Post_{Q}}) \Big)
-\end{split}
-\end{equation*}
-We conclude by observing that $\Post_Q$ has no effect on variables of $P$ and $P'$, and thus on $\Pred_{P,P' x}$
+(\forall j\in J_P.\, \vis{\beta_j}=\gamma_{j x} \land \forall j\in J_Q.\, \vis{\beta_j}=\vis{\beta_j} )\Rightarrow\\
+ (\Pred_{P' x}\land \Pred_Q\land \alpha_Q=\beta\land  \alpha_x=\alpha \land \Pred_{P,P' x}\subst{\Post_{P' x}\uplus\Post_P\uplus \Post_{Q}}) \Big)
+\end{multline*}
+We conclude by observing that $\Post_Q$ has no effect on variables of $P$ and $P'$, and thus on $\Pred_{P,P' x}$ and $\Pred$ leading to the conclusion about $\alpha_Q=\beta$.
 \end{proof}

### 2020-05-26 2016-Weak-FH-Bisim/WeakBisim.tex
correct part 1

@@
 \usepackage[T1]{fontenc}
+\usepackage{lmodern}
 %\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
@@
 While most of our previous works relied on closed, fully-instantiated semantics~\cite{BBCHM:article2008,AmeurBoulifa2017,HKM-FASE16}, it is only recently that we could design a first version of a  parameterised semantics for pNets with a strong bisimulation equivalence~\cite{henrio:Forte2016}.
-This article builds open this previous parameterised semantics and provide a cleaner version of the semantics with a slightly simplified formalism, adding a notion of global state to automata.
+This article builds open this previous parameterised semantics and provides a cleaner version of the semantics with a slightly simplified formalism, adding a notion of global state to automata.
 The slight simplification of the formula allowed us to adopt a much cleaner presentation where the theory for open automata, the algebra used to define the semantics of pNets with holes, can be studied independently from its application to pNets.
@@
 \item A theory of weak bisimulation for open automata, and its properties.
-It relies on the definition of weak open transitions that are derived from transitions of the open automaton by concatenating invisible action transitions with one (visible or not) transition.
+It relies on the definition of weak open transitions that are derived from transitions of the open automaton by concatenating invisible action transitions with one (visible or not) action transition.
 The precise definition of the concatenation is also a major contribution of this article.
@@
 set of \emph{synchronisation vectors} that express the possible
-synchronisation between the parameterised actions of a subset of the
-sub-trees.
+synchronisation between the parameterised actions of a subset of the sub-trees.
 
@@
 \item[$\bullet$] $\to \subseteq S \times L \times S$ is the transition relation and 
-$L$ is the set of labels of the form
+$L$ is the set of labels of the form:\\
 $\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in J}\rangle$,
@@
 
-pNets are composition entities equipped with a rich synchronisation mechanism: synchronisation vectors allows the expression of synchronisation between any number of entities and at the same time the passing of data between processes.
+pNets are composition entities equipped with a rich synchronisation mechanism: synchronisation vectors allow the expression of synchronisation between any number of entities and at the same time the passing of data between processes.
 Their strongest feature is that the data emitted by processes can be used can be used inside the synchronisation vector to do addressing: it is easy to synchronise a process indexed by $n$ with the action $a(v,n)$ of another process.
@@
 
-Fig. \ref{SimpleProt:Spec} (left) shows the example principle, which corresponds to the hierarchical structure of a pNet: two unspecified
+Figure \ref{SimpleProt:Spec} (left) shows the example principle, which corresponds to the hierarchical structure of a pNet: two unspecified
 processes $P$ and $Q$ (holes) communicate messages, with a data value
@@
 
-Fig. \ref{SimpleProt:Spec} (right) shows a graphical view of the pNet that specifies the system:
+Figure \ref{SimpleProt:Spec} (right) shows a graphical view of the pNet that specifies the system:
 the full system should be equivalent (e.g.  weakly bisimilar)
@@
 It consists of three nodes: two holes $P$ and $Q$ and one subnet, denoted {\it PrefectBuffer}.
-Nodes of the tree are synchronized using four synchronization vectors, that  express the possible synchronizations between the parameterized actions of a subset of the nodes.
+Nodes of the tree are synchronized using four synchronization vectors, that  express the possible synchronizations between the parameterised actions of a subset of the nodes.
 For instance, in the vector "$< \texttt{p-send(m)},\texttt{in(m)},\_> \rightarrow \texttt{\nounderline{in(m)}}$" only $P$ and {\it PrefectBuffer} nodes are involved in the synchronization.
@@
 	\begin{itemize}
-		\item[$\bullet$]   $J$ is a  set of indices,
+		\item[$\bullet$]   $J$ is a  set of indices.
 		\item[$\bullet$]   $\mathcal{S}$ is a set of states and $s_0$ an initial state
-		  among $\mathcal{S}$,
+		  among $\mathcal{S}$.
 %       \item[$\bullet$] for each state $s$, $vars(s)=\{v_s\}$ is a set of state variables, 
@@
    \mathcal{T}_1\!>$ and $<\!J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2\!>$ has the form $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$, it relates states of $\mathcal{S}_1$ and 
-$\mathcal{S}_2$ constrained by a predicate
-More precisely, for any pair $(s,t)\in S_1\times S_2$, there is a 
+$\mathcal{S}_2$ constrained by a predicate.
+More precisely, for any pair $(s,t)\in \mathcal{S}_1\times \mathcal{S}_2$, there is a 
    single
@@
 $\Post_{OT_x}$ that are independent), applying the assignments of the involved rules.
-We can prove that such a bisimulation is an equivalence relation:
+We can prove that such a bisimulation is an equivalence relation.
 
@@
 
-The proof of this theorem can be found in~\ref{thm-equiv-proof}. The
+The proof of this theorem can be found in Annex~\ref{thm-equiv-proof}. The
 only non-trivial part of the proof is the proof of transitivity. It
@@
   \triangleright| \forall i\in L. s_i \in S_i\}$.
-A pLTS being its own single leave:
+A pLTS being its own single leave:\\
   $States(\mylangle S,s_0,V, \to\myrangle) = \{\triangleleft s \triangleright| s \in S, \}$.  
@@
 
-\paragraph{Predicates:}
+\paragraph{\hl{Predicates:}} 
 %Let
@@
 %\TODO{Eric: rewrite example with new Protocolkeep only OT1, and adapt comments}
-\begin{example}[An open-transition]
+\begin{example}[\hl{An open-transition}]
   \label{OT:SimpleProt}
@@
       \{\texttt{P}\mapsto \texttt{p-send(m)}\},  [\texttt{m=m'}],
-        \{\texttt{s\_msg}\gets \texttt{m}\}
+        (\texttt{s\_msg}\gets \texttt{m})
                       }
@@
     \smallskip
-    The global states here are triples, build as the product of states of the 3 pLTS (remember the holes have no state). The assignment
+    The global states here are triples, build as the product of states of the 3 pLTSs (remember the holes have no state). The assignment
     $Post$ uses the variable $\texttt{m}$ from the action of hole $\texttt{P}$ to set the
@@
 
-	The rule for a pLTS  checks that the guard 
-	is verified and transforms assignments into post-conditions:		
+\begin{itemize}
+\item The rule for a pLTS  checks that the guard is verified and transforms assignments into post-conditions:		
 \begin{mathpar}\inferrule
@@
 
-	The second rule deals with pNet nodes: for each possible
+\item	The second rule deals with pNet nodes: for each possible
 	synchronisation vector (of index $k$) applicable to the rule subject, the premisses
@@
 \end{mathpar} 
+\end{itemize} 
 	\medskip
@@
 	expressed in terms of the leaves and holes of the pNet structure,
-	i.e. a flatten view of the pNet: e.g. $L$ is the index set of the
+	i.e. a flatten view of the pNet, e.g. $L$ is the index set of the
 	Leaves, $L_m$ the index set of the leaves of one subnet indexed $m$, so all $L_m$
@@
 Note that  the construction is symbolic, and each open-transition deduced expresses a whole family of
-behaviours, for any possible values of the variables.
+behaviours, for any possible value of the variables.
 %
@@
 
-We have shown in \cite{henrio:Forte2016} that an open-pNet
+We have shown in \cite{henrio:Forte2016} that an open pNet
 with finite synchronisation sets, finitely many leaves and
@@
    \centerline{\includegraphics[width=13cm]{XFIG/SPSpecOpen}}
-   \caption{Specification OA}
+   \caption{Specification Open Automaton}
    \label{SimpleProtCounter:SpecOA}
@@
 In this drawing, we have short labels for states, representing $\ostate{s_0,m_0,r_0}$ by \texttt{000}.
-Note that open transitions are denoted $\texttt{OT}_i$ and tau open transition by  $\texttt{OT}_{\tau}$.
+Note that open transitions are denoted $\texttt{SI}_i$ and tau open transition by  $\texttt{SI}_{\tau}$.
 The resulting behavior is quite simple:  we have a main loop including receiving a message from $P$ and transmitting the same message to $Q$, with some intermediate $\tau$ actions from the internal communications between the protocol processes.
 In most of the transitions, you can observe that data is propagated between the successive state variables (holding the message, and the error counter value).
-On the right of the figure, you have a loop of $\tau$ actions ($\texttt{OT}_4$, $\texttt{OT}_5$ and $\texttt{OT}_6$)  showing the handling of errors and corresponding increments of the error counter.
+On the right of the figure, you have a loop of $\tau$ actions ($\texttt{SI}_4$, $\texttt{SI}_5$ and $\texttt{SI}_6$)  showing the handling of errors and corresponding increments of the error counter.
 
@@
 Note that this does not mean that any two pNets can be composed and produce an open 
-transition. Indeed, the predicate $\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0}$ is often not  satisfiable, for example if the action  $\alpha_Q$ cannot be matched with $\beta_{j_0}$.
+transition. Indeed, the predicate $\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0}$ is often not  satisfiable, in particular if the action  $\alpha_Q$ cannot be matched with $\beta_{j_0}$.
 Note also that $\beta_{j_0}$ is  only used as an intermediate term inside formulas in the composed open transition: it 
@@
 \begin{definition}[FH-bisimulation for open pNets]\label{def:bisim-pnets}
-Two pNets are FH-bisimilar if there exist a relation between their associated 
+Two pNets are FH-bisimilar if there exists a relation between their associated 
 automata that is an FH-bisimulation and their initial states are in the relation (i.e. the predicate associated with the initial states is verifiable).
@@
 Their values thus depend on the initial state but also on the effect (as a substitution $\Post_1$) of the first weak open transition.
-In the same manner, $\Pred_3$ must be applied the joint substitution $\Post_2\bigotimes\Post_1$.
+In the same manner, $\Pred_3$ must be applied the joint substitution $\Post_2\shortotimes\Post_1$.
 Similarly, effects on variables must be applied to obtain the global effect of the composed weak open transition, it must also be applied to observable actions of the holes, and to the global action of the weak open transition.
@@
 
-\begin{example}
-  Figure \ref{WOT2} shows the construction of one of the weak transitions of the Specification OA.
+\begin{example} Figure \ref{WOT2} shows the construction of one of the weak transitions of the Specification OA.
 On the top we show the subset of the original open automaton (from Figure \ref{SimpleProtCounter:SpecOA}) considered here, and at the bottom the generated weak transition.
@@
 			(\texttt{ec}\gets \texttt{ec}+n) }
-        {\text{b1} \OTWeakarrow \tau \text{b1}} \forall n \geq 0$.
-Finally,  applying again \WTTrois, and using the central open transition having \texttt{\nounderline{out(b\_m,b\_ec)}}  as $\alpha$, we get the resulting weak open transition between b1 and b0 (as shown in Figure \ref{WOT2}).
-Applying the substitutions finaly yields the weak transition $WS_7$ in Figure  \ref{SimpleProtCounter:WeakSpecOA}.
+        {\text{b1} \OTWeakarrow \tau \text{b1}}\, \forall n \geq 0$.
+Finally,  applying again \WTTrois, and using the central open transition having \texttt{\nounderline{out(b\_msg,b\_ec)}}  as $\alpha$, we get the resulting weak open transition between b1 and b0 (as shown in Figure \ref{WOT2}).
+Applying the substitutions finally yields the weak transition $WS_7$ in Figure  \ref{SimpleProtCounter:WeakSpecOA}.
 
@@
 We concentrate on weak open transitions $WI_3$ and $WI_4$.
-Let us denote as $post_n$ the effect (= substitution) of the strong open transitions $SI_n$ from Figure \ref{SimpleProtCounter:ImplOA}:
+Let us denote as $post_n$ the effect (substitution) of the strong open transitions $SI_n$ from Figure \ref{SimpleProtCounter:ImplOA}:
 \smallskip
@@
 = (\texttt{s\_ec}\gets \texttt{s\_ec}+1)$.
-\footnote{when showing  the result of $Posts$ composition, we will systematicaly omit the identity substitutions introduced bythe $\shortotimes$ definition in page \pageref{def:substitutions}}
+\footnote{when showing  the result of $Posts$ composition, we will Z omit the identity substitutions introduced bythe $\shortotimes$ definition in page \pageref{def:substitutions}}
 \medskip
@@
 These are however technically more complex than the ones for open automata because each hole performs a set of actions, and thus a composed transition is the composition of one transition of the top-level pNet and a sequence of transitions of the sub-pNet that fills its hole.
-They can be found as Lemmas~\ref{lem-decomposeWOT}, Lemma~\ref{lem-Weakcompose1}, and Lemma~\ref{lem-Weakcompose} in~\ref{sec:app-composition}.
+They can be found as Lemmas~\ref{lem-decomposeWOT}, Lemma~\ref{lem-Weakcompose1}, and Lemma~\ref{lem-Weakcompose} in Appendix~\ref{sec:app-composition}.
 
@@
 \subsection{Running example}
-In section \ref{def:weakOT} we have shown the full satured weak automaton for both the specification and the implementation of the simple protocol.
+In section \ref{sec:weak} we have shown the full satured weak automaton for both the specification and the implementation of the simple protocol.
 We will show here how we can check if some given relation between these two automata is a weak FH-Bisimulation.

### 2020-05-27 2016-Weak-FH-Bisim/WeakBisim.tex
typos

@@
 \AlgE\cap\AlgA=\emptyset$;
-naturally action terms will use data expressions as subterms.
+naturally action terms will use data expressions as sub-terms.
 
@@
 
-pNets are tree-like structures, where the leaves are either
-\emph{parameterised labelled transition systems (pLTSs)}, expressing the
+pNets are tree-like structures, where the leaves are either \emph{parameterised labelled transition systems (pLTSs)}, expressing the
 behaviour of basic processes, or \emph{holes}, used as placeholders
@@
 %actions, this set is named the \emph{sort}.
-Nodes of the tree (pNet nodes) are synchronising artifacts, using a
+Nodes of the tree (pNet nodes) are synchronising artefacts, using a
 set of \emph{synchronisation vectors} that express the possible
@@
 
-Each sub-pNets expose
+Each sub-pNet exposes
 a set of actions, called \emph{internal actions}. The synchronisation between global actions exposed by the pNet and
@@
 
-Fig.
-\ref{SimpleProt:Impl} shows the pNet model of the protocol implementation.
+Figure \ref{SimpleProt:Impl} shows the pNet model of the protocol implementation.
 When the $\symb{Medium}$ detects an error (modelled by a local $\tau$ action), it sends back a $\texttt{m\_error}$ message to the $\symb{Sender}$.
@@
  We name it FH-bisimulation,
- as a short cut for the ``Formal Hypotheses'' over the holes behavior manipulated in the
+ as a short cut for the ``Formal Hypotheses'' over the holes behaviour manipulated in the
  transitions, but also as a reference to the work of De Simone~\cite{deSimone85},
@@
 \subsubsection*{Note on finite versus infinite open automata:} 
-As mentioned in Definition \pageref{def:open-automaton}, we adopt here a semantic view on open automata. More precisely, in \cite{hou:hal-02406098}, we formely define
+As mentioned in Definition \pageref{def:open-automaton}, we adopt here a semantic view on open automata. More precisely, in \cite{hou:hal-02406098}, we formerly define
 \emph{semantic open automata} (infinite as in Definition \ref{def:open-automaton}),
@@
 The definition of bisimulation for open automata allows us to derive a
-bismulation theory for open pNets. As pNets are composition
+bisimulation theory for open pNets. As pNets are composition
 structures, it then makes sense to prove composition lemmas: we prove
@@
 Note that open transitions are denoted $\texttt{SI}_i$ and tau open transition by  $\texttt{SI}_{\tau}$.
-The resulting behavior is quite simple:  we have a main loop including receiving a message from $P$ and transmitting the same message to $Q$, with some intermediate $\tau$ actions from the internal communications between the protocol processes.
+The resulting behaviour is quite simple:  we have a main loop including receiving a message from $P$ and transmitting the same message to $Q$, with some intermediate $\tau$ actions from the internal communications between the protocol processes.
 In most of the transitions, you can observe that data is propagated between the successive state variables (holding the message, and the error counter value).
@@
 = (\texttt{s\_ec}\gets \texttt{s\_ec}+1)$.
-\footnote{when showing  the result of $Posts$ composition, we will Z omit the identity substitutions introduced bythe $\shortotimes$ definition in page \pageref{def:substitutions}}
+\footnote{when showing  the result of $Posts$ composition, we will Z omit the identity substitutions introduced by the $\shortotimes$ definition in page \pageref{def:substitutions}}
 \medskip
@@
 = (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_msg}+1+n), \forall n\ge 0$
-
 \medskip  
-$ WI_{8c}(n) = \openrule
+$WI_{8c}(n) = \openrule
          {\{\texttt{Q}\mapsto \texttt{q-recv(s\_msg,s\_ec}+n)\}, True, (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_msg}+1+n)}
-         {210 \OTWeakarrow {\nounderline{\texttt{out(s\_msg,s\_ec}+n)}} 202}\forall n\ge 0
-        $
+         {210 \OTWeakarrow {\nounderline{\texttt{out(s\_msg,s\_ec}+n)}} 202}\forall n\ge 0$
 
@@
       sub-net are of the form ``$< -, \tau, -> -> \tau$''.
-    \item We must take care of variable name conflicts: in our example, the state variables of the 2 systems already have different names, but the action parameters occuring in the transitions (m, msg, ec) are the same, that is not correct.
+    \item We must take care of variable name conflicts: in our example, the state variables of the 2 systems already have different names, but the action parameters occurring in the transitions (m, msg, ec) are the same, that is not correct.
 In the tools, this is managed by the static semantic layer; in the following example, we have renamed all conflicting variables with 1 for the Spec, and 2 for the Impl.
@@
 
-To the best of our knowledge, there is no other research works on the Bisimulation Equivalence between such complicate(open, symbolic, parameterized, with loops and assignments) system models, with providing fully complete algorithms.
+To the best of our knowledge, there is no other research works on the Bisimulation Equivalence between such complicate(open, symbolic, parameterised, with loops and assignments) system models, with providing fully complete algorithms.
 For the sake of completeness, we give a brief overview of other Symbolic Bisimulation researches.
@@
 \label{section:conclusion}
- pNets (Parameterised Networks of Automata) is a formalism adapted to the representation of the behavior of a parallel or distributed systems.
-One  strength of pNets is their parameterized nature, making them adapted to the representation of systems of arbitrary size, and making the modelling of parameterized system possible.
+ pNets (Parameterised Networks of Automata) is a formalism adapted to the representation of the behaviour of a parallel or distributed systems.
+One  strength of pNets is their parameterised nature, making them adapted to the representation of systems of arbitrary size, and making the modelling of parameterised system possible.
 Parameters are also crucial to reason on interaction protocols that can address one entity inside an indexed set of processes.
@@
 
-Open pNets are pNets with holes; they are adapted to represent processes parameterized by the behaivour of other processes, like composition operators or interaction 
+Open pNets are pNets with holes; they are adapted to represent processes parameterised by the behaivour of other processes, like composition operators or interaction 
 protocols that synchronize the actions of processes that can be plugged afterwards. Open
@@
 
-This article defines a strong and a weak bisimulation principles that are adapted to parameterized systems and hierarchical composition.
+This article defines a strong and a weak bisimulation principles that are adapted to parameterised systems and hierarchical composition.
 Our bisimulation principle handles pNets parameters in the sense that two states might be or not in relation depending on the value of parameters.
@@
 \end{enumerate}
-By using  Lemma \ref{lem-rel-OT-WOT}, and denoting $\displaystyle{J=\bigcup_{i=0}^{m_1}J_{1i}\cup J_2\cup \bigcup_{i=0}^{m_2}J_{3i}}$, we can conclude from cases 1, 2 and 3 that we have:
+By using  Lemma \ref{lem-rel-OT-WOT}, and denoting $\displaystyle{J=\bigcup_{i=0}^{m_1}J_{1i}\cup J_2\cup \bigcup_{i=0}^{m_2}J_{3i}}$, we can conclude from cases (1), (2) and (3) that we have:
 \begin{mathpar}
@@
 Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha'_p$ some of them may be non-observable (they are $\tau$ transitions).
-By considering the sequence of $\tau$ and non-$\tau$ actions we split the sequence of actions into $n+1$ subsequences, such that each subsequence is a sequence of actions containing  only one observable action that will be named $\alpha_p$, and possibly many non-observable ($\tau$) ones.
+By considering the sequence of $\tau$ and non-$\tau$ actions we split the sequence of actions into $n+1$ sub-sequences, such that each subsequence is a sequence of actions containing  only one observable action that will be named $\alpha_p$, and possibly many non-observable ($\tau$) ones.
 
@@
 
- We can decompose each of the $n+1$ subsequences in the following way (see Figure~\ref{figproof}).
+ We can decompose each of the $n+1$ sub-sequences in the following way (see Figure~\ref{figproof}).
 For $k\in [0..n]$ the position of the $k^{\text{th}}$ visible action is  $n_k$.
 For $l\in [1..n]$,  $n'_l$ is any index between $n_{l-1}$ and $n_l$, additionally $n'_0=0$ and $n'_{n+1}=n_1+n_2+3$.
-We obtain $n+1$ subsequences  made of the following OTs, for all $k\in [0..n]$ :\\
+We obtain $n+1$ sub-sequences  made of the following OTs, for all $k\in [0..n]$ :\\
 \begin{small}
@@
 \end{mathpar}
-With:
+with:
 {\small
@@
 \alpha_k\displaystyle{\subst{\!\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}}\]
-With~\ref{eqproofbeta}, we now have. Recall that the actions $\alpha_k$ are the actions $\alpha'_{p}$ that are observable: 
+\hl{With}~\ref{eqproofbeta}, we now have. Recall that the actions $\alpha_k$ are the actions $\alpha'_{p}$ that are observable: 
 \begin{eqnarray*}
@@
 		}\]
-With
+with
 \[  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) \qquad\text{trivial}\]
@@
 
-It is based on the observation that states 202 and 000 are only linked by a "pure $\tau$" transition, and have exactly the same possible behaviors.
+It is based on the observation that states 202 and 000 are only linked by a "pure $\tau$" transition, and have exactly the same possible behaviours.
 More tricky, they do not have the same state variables, as 202 has the variables of state $s2$, but none of these variables are used in transitions from 202.
-In this configuration we can garantee that they are Weak Bisimilar, and merge their (incoming and outgoing) transitions in the Figure. We denote this 
+In this configuration we can guarantee that they are Weak bisimilar, and merge their (incoming and outgoing) transitions in the Figure. We denote this 
 equivalence class of states as $\{000,202\}$.
-\TODO{May be express this property more formely, but this could be also part of another paper, more oriented towards algorithms and optimisation of the Weak}
+\TODO{May be express this property more formerly, but this could be also part of another paper, more oriented towards algorithms and optimisation of the Weak}
 

### 2020-06-03 2016-Weak-FH-Bisim/WeakBisim.tex
abstract

@@
 
-This article defines bisimulation relations for the pNet model, to compare  systems described using the pNets model.
- We define a strong bisimulation for open pNets.
+This article defines bisimulation relations for the pNet modelfor the comparison of systems specified as pNets.
+ We first define a strong bisimulation for open pNets.
   In practice, as happens in process algebras, strong bisimulation is too strong, and
@@
   the classical \emph{weak bisimulation}, and study its properties.
-
-Amon these properties we show compositionality: If two systems are proven equivalent they will be undistinguishable by their context, and they will also be undistinguishable when their holes are filled with equivalent systems.
-
-  Which significant (small) use-case ?
-
+Among these properties we are interested in compositionality: If two systems are proven equivalent they will be undistinguishable by their context, and they will also be undistinguishable when their holes are filled with equivalent systems.
+The article is illustrated with a running example showing the characteristics of our formalism and our bisimulation relations.
 \end{abstract}
@@
 \maketitle
-
-\section*{Status and TODO list}
-
-TODOS: AVRIL 2019
-
-- exemple (Eric: failure buffer)
-- biblio (rabea)
-- inuitions de preuves et intuition de bisim de cloture, etc. (Ludo)
-
-%% \TODO{voisr si on redefinit les bigotimes pour prendre des maps et retourner des maps au lieu des substitutions (et on englobe dans une subst a la fin)}
-
-%% \TODO{prendre soin des posts sur les actions partout}
-
-%% ===> dealine 14 Juillet
-
-%% TODOs du 19 decembre
-
-%% - enlever 5.2 et citer avocs
-
-%% - ajouter des proof sketch dans le papier
-
-%% - def 11 point 2:
-%% A, Pred, Post
-%% -----------   in T
-%% s->s'
-%% et A(j)=tau
-%% implies blablabla
-
-%% OLD OLD OLD (check)
-%% Notes de reunion 24 Sept
-
-%% - etat de l art: il faudrait des refs sur bisim en gemneral, probablement avec pas mal de pi calcul (Eric?), des refs sur pourquoi pnets et des refs sur utilite de la weak bisim en verif
-
-%% - target: JLamp
-
-%% Conventions
-%% [14/9/2018]
-
-%% Dans le texte pas de $\backslash$ devant pNet et pLTS
-
-%% pNet devient P ou Q dans les equations; on garde $pLTS$
-
-%% \medskip
-
-%% TODOS et deadline
-
-%% Global and questions:
-%% \begin{itemize}
-%% \item \TODO{should we use iff/implies or LeftRightArrow/Rightarrow}
-%% \item related works
-%% \end{itemize}
-%% Ludo:
-%% \begin{itemize}
-%% \item[X] reorga sec weak bisim + thm -> 10 Juil
-%% \item[X]  intro et orga globale du papier -> fin aout
-%% \item[partial] explication dans semantique open pnets et composition
-%% \item uniformisation pNet P Q
-%% \end{itemize}
+%
+%\section*{Status and TODO list}
+%
+%TODOS: AVRIL 2019
+%
+%- exemple (Eric: failure buffer)
+%- biblio (rabea)
+%- inuitions de preuves et intuition de bisim de cloture, etc. (Ludo)
+%
+%%% \TODO{voisr si on redefinit les bigotimes pour prendre des maps et retourner des maps au lieu des substitutions (et on englobe dans une subst a la fin)}
+%
+%%% \TODO{prendre soin des posts sur les actions partout}
+%
+%%% ===> dealine 14 Juillet
+%
+%%% TODOs du 19 decembre
+%
+%
+%
+%%% - enlever 5.2 et citer avocs
+%
+%%% - ajouter des proof sketch dans le papier
+%
+%%% - def 11 point 2:
+%%% A, Pred, Post
+%%% -----------   in T
+%%% s->s'
+%%% et A(j)=tau
+%%% implies blablabla
+%
+%
+%%% OLD OLD OLD (check)
+%%% Notes de reunion 24 Sept
+%
+%
+%%% - etat de l art: il faudrait des refs sur bisim en gemneral, probablement avec pas mal de pi calcul (Eric?), des refs sur pourquoi pnets et des refs sur utilite de la weak bisim en verif
+%
+%
+%
+%%% - target: JLamp
+%
+%%% Conventions
+%%% [14/9/2018] 
+%
+%%% Dans le texte pas de $\backslash$ devant pNet et pLTS
+%
+%%% pNet devient P ou Q dans les equations; on garde $pLTS$
+%
+%%% \medskip
+%
+%%% TODOS et deadline
+%
+%
+%%% Global and questions:
+%%% \begin{itemize}
+%%% \item \TODO{should we use iff/implies or LeftRightArrow/Rightarrow}
+%%% \item related works
+%%% \end{itemize}
+%%% Ludo:
+%%% \begin{itemize}
+%%% \item[X] reorga sec weak bisim + thm -> 10 Juil
+%%% \item[X]  intro et orga globale du papier -> fin aout
+%%% \item[partial] explication dans semantique open pnets et composition
+%%% \item uniformisation pNet P Q
+%%% \end{itemize}
+%
+%
 

### 2020-06-03 2016-Weak-FH-Bisim/WeakBisim.tex
skype

@@
 Among these properties we are interested in compositionality: If two systems are proven equivalent they will be undistinguishable by their context, and they will also be undistinguishable when their holes are filled with equivalent systems.
-The article is illustrated with a running example showing the characteristics of our formalism and our bisimulation relations.
+The article is illustrated with a transport protocol running example; it shows the characteristics of our formalism and our bisimulation relations.
 \end{abstract}
@@
 While most of our previous works relied on closed, fully-instantiated semantics~\cite{BBCHM:article2008,AmeurBoulifa2017,HKM-FASE16}, it is only recently that we could design a first version of a  parameterised semantics for pNets with a strong bisimulation equivalence~\cite{henrio:Forte2016}.
-This article builds open this previous parameterised semantics and provides a cleaner version of the semantics with a slightly simplified formalism, adding a notion of global state to automata.
-The slight simplification of the formula allowed us to adopt a much cleaner presentation where the theory for open automata, the algebra used to define the semantics of pNets with holes, can be studied independently from its application to pNets.
+This article builds upon this previous parameterised semantics and provides a cleaner version of the semantics with a slightly simplified formalism.
+It also adds a notion of global state to automata.
+The slight simplification of the formalism allowed us to adopt a much cleaner presentation where the theory for open automata.
+The algebra used to define the semantics of pNets with holes, can be studied independently from its application to pNets.
 Also, in \cite{henrio:Forte2016} the study of compositionability was only partial, and in particular the proof that bisimulation is an equivalence is one new contribution of this article and provides a particularly interesting insight on the semantic model we use.
@@
 This allows us to define a weak bisimulation equivalence for open pNets with valuable properties of compositionality.
-To summarise, the contribution of this paper are the following
+To summarise, the contribution of this paper are the following:
 \begin{itemize}
-\item The definition of open automata: an algebra of parameterised automata with hole with a strong bisimulation equivalence.
+\item The definition of open automata: an algebra of parameterised automata with holes, and a strong bisimulation equivalence.
 This is an adaptation of~\cite{henrio:Forte2016} with an additional property stating that strong bisimulation equivalence is indeed an equivalence relation.
@@
  expressions $\AlgE$, including a set of boolean
-expressions $\AlgE$ ($\AlgB\subseteq\AlgE$). We let $e_i$ range over expressions ($e_i\in\AlgE$).
+expressions $\AlgE$ ($\AlgB\subseteq\AlgE$). 
 On top of $\AlgE$ we build the action algebra
@@
 naturally action terms will use data expressions as sub-terms.
-
-Let $a$
+The function
+$\vars(t)$ identifies the set of variables in a term
+$t\in\AlgT$.
+
+We let $e_i$ range over expressions ($e_i\in\AlgE$), $a$
 range over action labels, $\symb{op}$ be operators, and $x_i$ and $y_i$ range over
@@
 appear somewhere else in the same action term:
-$p_i=?x\Rightarrow\forall j\neq i.\, x\notin \vars(p_j)$
-
-The set of actions that do not distinguish input variables is denoted $\AlgAS$, it will be used in synchronisation vectors of pNets below:
+$p_i=?x\Rightarrow\forall j\neq i.\, x\notin \vars(p_j)$.
+We define $iv(t)$  as the set of input variables of a term $t$ (without the '?' marker).
+Action algebras can encode naturally usual point-to-point message passing calculi (using 
+$a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs), but it also allows
+for more general synchronisation mechanisms, like gate negociation in Lotos, or broadcast
+communications.
+
+The set of actions that do not distinguish input variables is denoted $\AlgAS$, it will be used in synchronisation vectors of pNets:
 \[\begin{array}[l]{rcl@{\quad}l}
@@
 \]
-
-The function
-$\vars(t)$ identifies the set of variables in a term
-$t\in\AlgT$, and $iv(t)$ returns the name of its input variables (without the '?' marker).
-Action algebras can encode naturally usual point-to-point message passing calculi (using 
-$a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs), but it also allows
-for more general synchronisation mechanisms, like gate negociation in Lotos, or broadcast
-communications.
 
@@
 indexed structures are always denoted with an exponent of the form $i\in I$.
+
 Consequently, $a_i^{i\in I}$ defines first $I$ the set over which the
 family is indexed, and then $a_i$ the elements of the family.
-
 For example $a^{i\in\{3\}}$ is
@@
 %now corresponds to $a$.
+
 When this is not ambiguous, we shall use abusive vocabulary and
@@
 %An empty family is denoted $[]$. % (it can be defined as $a_i^{i\in\emptyset}$).
-To simplify equations, an indexed set can be denoted $\set{M}$
-instead of $M_l^{l\in L}$ when $L$ is irrelevant.
+To simplify equations, an indexed set can be denoted $\set{a}$
+instead of $a_i^{i\in I}$ when $I$ is irrelevant.
 
@@
 The set of holes $\Holes(\pNet)$ of a pNet is the indexes of the holes of the pNet 
-itself plus the indexes of all the holes of its subnets.
+itself plus the indexes of all the holes of its sub-pNets.
 It is defined inductively (we suppose those indexes 
@@
 The actions on the \pLTS s can send or receive values, potentially modifying the value of variables.
-pNets are synchronisation entities: a pNet composes several subnets and  synchronisation vectors define how the subnets interact, where a subnet is either a pNet or a pLTS.
-Synchronisation between subnets is defined by synchronisation vectors that express how an action of a subnet can be synchronised with actions of other subnet, and how the resulting synchronised action is visible to the outside of the pNet.
-Synchronisation vectors also allow to explicitly export an action of a subnet to the next level, or to allow to subnets to synchronise and only exporting a non-observable action (provided such an non-visible action labels exist in the action algebra.
-Finally, a pNet can leave subnets undefined and instead declare holes with a well-defined signature.
-Holes can then be filled with a subnet.
+pNets are synchronisation entities: a pNet composes several sub-pNets and  synchronisation vectors define how the sub-pNets interact, where a sub-pNet is either a pNet or a pLTS.
+Synchronisation between sub-pNets is defined by synchronisation vectors that express how an action of a sub-pNet can be synchronised with actions of other sub-pNet, and how the resulting synchronised action is visible to the outside of the pNet.
+Synchronisation vectors can also express the exportation of an action of a sub-pNet to the next level, or to hide an interaction and make it non-observable.
+Finally, a pNet can leave sub-pNets undefined and instead declare holes with a well-defined signature.
+Holes can then be filled with a sub-pNet.
 This is defined as follows.
@@
 It acts as the parallel operator.
-It consists of three nodes: two holes $P$ and $Q$ and one subnet, denoted {\it PrefectBuffer}.
+It consists of three nodes: two holes $P$ and $Q$ and one sub-pNet, denoted {\it PrefectBuffer}.
 Nodes of the tree are synchronized using four synchronization vectors, that  express the possible synchronizations between the parameterised actions of a subset of the nodes.
@@
 This section defines open automata and a bisimulation theory for them.
-This section can be viewed as an improved version of the formalism described in \cite{henrio:Forte2016}, generalising the automata with a notion of global variable, which makes the state of the automaton more explicit.
+This section can be viewed as an improved version of the formalism described in \cite{henrio:Forte2016}, extending the automata with a notion of global variable, which makes the state of the automaton more explicit.
 We also adopt a semantics and logical interpretation of the automata that intuitively can be stated as follows: ``if a transition belongs to an open automaton, any refinement of this transition also belongs to the automaton''.
@@
        $\beta_j$ and $\alpha$. \Post\ is a set of 
-	assignments that are effective \emph{after the open transition}, they are
+	assignments that are effective after the open transition, they are
         represented as a substitution of the form $({x_k\gets e_k})^{k\in K}$ 
@@
 	An \emph{open automaton} is a structure\\ $A =
-	<J,\mathcal{S},s_0,V,\mathcal{T}>$ where:
+	<\!J,\mathcal{S},s_0,V,\mathcal{T}\!>$ where:
 	\begin{itemize}
@@
 The equivalence we need is a strong bisimulation between
-open automata having exactly the same holes with the same sorts, but using a
+open automata having exactly the same holes (same indexes and same sorts), but using a
 flexible matching 
@@
       True, i.e. the states are related when the variables in $V_1$ and $V_2$ verify the 
-      predicate $\Pred_{s,t}$. By nature, this is only correctly defines if the variales of the two open automata are disjoint, i.e.  $V_1\cap V_2=\emptyset$.
+      predicate $\Pred_{s,t}$. By nature, this is well-defined if the variales of the two open automata are disjoint, i.e.  $V_1\cap V_2=\emptyset$.
  FH-bisimulation is defined formally: 
@@
 \noindent
-\begin{minipage}{0.69\linewidth} 	Suppose that
+\begin{minipage}{0.69\linewidth} 	Suppose 
    $A_1 = <\!J,\mathcal{S}_1, s_0,V_1,
@@
 
-\subsubsection*{Note on finite versus infinite open automata:} 
+\subsubsection*{Finite versus infinite open automata, and decidability:} 
 As mentioned in Definition \pageref{def:open-automaton}, we adopt here a semantic view on open automata. More precisely, in \cite{hou:hal-02406098}, we formerly define
@@
 If we assume that everything is finite (states and transitions in the
-open automata, and the predicates in $\mathcal{R}$, then it is easy to
+open automata, and the predicates in $\mathcal{R}$), then it is easy to
 prove that it is decidable whether a relation is a 
 FH-bisimulation, provided the logic of the predicates is
-decidable (proof in \cite{henrio:Forte2016}). Formally:
+decidable (proof can be found in \cite{henrio:Forte2016}). Formally:
 
@@
 A pLTS being its own single leave:\\
-  $States(\mylangle S,s_0,V, \to\myrangle) = \{\triangleleft s \triangleright| s \in S, \}$.  
+  $States(\mylangle S,s_0,V, \to\myrangle) = \{\triangleleft s \triangleright| s \in S \}$.  
 %This could be encoded as a mapping from variables of the pNet to expressions, of the form: $\sigma=\{x_i\to e_i\}^{i\in I},\,(x_i\in vars(S))$.
@@
 
-\paragraph{\hl{Predicates:}} 
+\subsubsection*{Predicates} 
 %Let
@@
 %\TODO{Eric: rewrite example with new Protocolkeep only OT1, and adapt comments}
-\begin{example}[\hl{An open-transition}]
+\begin{example}[An open-transition]
   \label{OT:SimpleProt}
 At the upper level, the $\symb{SimpleSystem}$ pNet of Figure \ref{SimpleProt:Impl} has 2 holes and $\symb{SimpleProtocol}$ as
-a subnet, itself containing 3 pLTSs. One of its possible open transitions
+a sub-pNet, itself containing 3 pLTSs. One of its possible open transitions
 (synchronizing the hole $P$
@@
 	with the resulting action of the vector. The sub-pNets involved are split between two 
-	sets, $I_2$ for subnets that are pLTSs, and $I_1$ for the others, $J$ is the set of 
+	sets, $I_2$ for sub-pNets that are pLTSs, and $I_1$ for the others, $J$ is the set of 
 	holes involved in the transition\footnote{Formally, if $SV_k \!=\! \SV{({\alpha'})_m^{m 
@@
         	A key to understand this rule is that the open transitions are
-	expressed in terms of the leaves and holes of the pNet structure,
-	i.e. a flatten view of the pNet, e.g. $L$ is the index set of the
-	Leaves, $L_m$ the index set of the leaves of one subnet indexed $m$, so all $L_m$
+	expressed in terms of the leaves and holes of the whole pNet structure,
+	i.e. a flatten view of the pNet. For example, $L$ is the index set of the
+	Leaves, $L_m$ the index set of the leaves of one sub-pNet indexed $m$, so all $L_m$
 	are disjoint subsets of $L$. Thus the states in the open transitions,
@@
 	\set{\symb{SV}}\myrangle$.
-	Let $j_0\in J$ be a hole. Let $\pNetQ$ and $\pNetQ'$ be two FH-bisimilar pNets such that 
-	$\Sortop(\pNetQ)=\Sortop(\pNetQ')=\Sort_{j_0}$\footnote{Note that $\Sortop(\pNetQ)=\Sortop(\pNetQ')$ is 
+	Let $j_0\in J$ be a hole. Let $\pNetQ$ and $\pNetQ'$ be two FH-bisimilar pNets such that\footnote{Note that $\Sortop(\pNetQ)=\Sortop(\pNetQ')$ is 
 	ensured by 
-	strong bisimilarity.}. Then 
+	strong bisimilarity.} 
+	$\Sortop(\pNetQ)=\Sortop(\pNetQ')=\Sort_{j_0}$. Then 
 	$\pNet[\pNetQ]_{j_0}$ and 
@@
 \begin{theorem}[Context equivalence]\label{thm-ctxt-eq}
-	Consider two FH-bisimilar open pNets:
+	Consider two  open pNets
 	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
@@
 	\Sort_j^{j\in 
-	J}, 	\set{\symb{SV'}}\myrangle$ 
+	J}, 	\set{\symb{SV'}}\myrangle$ that are FH-bisimilar
 	(recall they must have the same holes to be bisimilar).
@@
 More precisely, we state that $\tau$ is not observable if the automaton always allows any $\tau$ transition from holes, and additionally the global transition resulting from a $\tau$ action of a hole is a $\tau$ transition not changing the pNet's state.
-We define $\Id(V)$ as the identity function on variables of $V$.
-\begin{definition}[Non-observability of $\tau$ actions]\label{def:Non-ObsTau}
+We define $\Id(V)$ as the identity function on the set of variables $V$.
+\begin{definition}[Non-observability of $\tau$ actions for open automata]\label{def:Non-ObsTau}
 An open automaton $A = <J,\mathcal{S},s_0,V,\mathcal{T}>$ \emph{cannot observe $\tau$ actions} if and only if for all $j$ in $J$ and $s$ in $\mathcal{S}$ we have:
@@
 Thus, we let $\gamma$ range over sequences of action terms and use $\dotcup$ as the concatenation operator that appends sequences of action terms: given two sequences of action terms  $\gamma\dotcup\gamma '$ concatenates the two sequences.
-The operation is lifted to indexed sets of sequences:  $\set {\gamma_1}\dotcup \set {\gamma_2}$ is an indexed set such that, at each index $i$, $\set {\gamma_1}\dotcup \set {\gamma_2}$ concatenates the sequences of actions at index $i$ of $\set{\gamma_1}$ and the one at index $i$ of $\set {\gamma_2}$\footnote{One of the two sequences is empty when $i\not \in \dom(\set{\gamma_1})$ or $i\not \in \dom(\set{\gamma_2})$ .}.
+The operation is lifted to indexed sets of sequences:   at each index $i$, $\set {\gamma_1}\dotcup \set {\gamma_2}$ concatenates the sequences of actions at index $i$ of $\set{\gamma_1}$ and the one at index $i$ of $\set {\gamma_2}$\footnote{One of the two sequences is empty when $i\not \in \dom(\set{\gamma_1})$ or $i\not \in \dom(\set{\gamma_2})$ .}.
 $[a]$ denotes a sequence with a single element.
@@
 
-As an example the $\vis{\set\beta}$ built from the transition $OT_1$ in page \pageref{OT:SimpleProt} is $\texttt{P}\mapsto [\texttt{p-send(m)}]$.
+As an example the $\vis{\set\beta}$ built from the transition $OT_1$ in Example~\ref{OT:SimpleProt}, page \pageref{OT:SimpleProt} is $\texttt{P}\mapsto [\texttt{p-send(m)}]$.
 Remark that in our simple example no $\tau$ transition involves any visible action from a hole, so we have no $\beta$ sequences of length longer than 1 in the weak automaton.
@@
 
-A weak open transition labelled $\alpha$ can be seen as a sequence of open transitions that are all labelled $\tau$ except one that is labelled $\alpha$; however conditions on predicates, effects, and states must be verified for this sequence to be enactable.
+A weak open transition labelled $\alpha$ can be seen as a sequence of open transitions that are all labelled $\tau$ except one that is labelled $\alpha$; however conditions on predicates, effects, and states must be verified for this sequence to be fired.
 
@@
   Let $A = <J,\mathcal{S},s_0,V,\mathcal{T}>$ be an open automaton. 
-The weak open automaton \emph{derived} from $A$ is an open automaton  $<J,\mathcal{S},s_0,V,\WT>$ where $\WT$ is derived from $\mathcal{T}$ as follows: 
+The weak open automaton \emph{derived} from $A$ is an open automaton  $<J,\mathcal{S},s_0,V,\WT>$ where $\WT$ is derived from $\mathcal{T}$ by saturation, applying the following rules.
 %\noindent{\bf Invisible $\tau$ transitions:}
@@
          {
-           \emptyset,\symb{True},\Id(s)}
+           \emptyset,\symb{True},\Id(V)}
          {s \OTWeakarrow {\tau} s} \in \WT  \qquad \WTUn
@@
 \end{definition}
-Rule $\WTUn$ states that it is always possible to do a null $\tau$ transition, where the state is unchanged and the holes perform no action.
+Rule $\WTUn$ states that it is always possible to do a non-observable transition, where the state is unchanged and the holes perform no action.
 Rule~$\WTDeux$ states that each open transition can be considered as a weak open transition.
@@
 
-$ WI_{6a}(n) = \openrule
+\begin{align*}
+WI_{6a}(n) =& \openrule
          {\{\}, True, 
@@
          {220 \OTWeakarrow {\tau} 210} \forall n\ge 0
-         $
-
-\medskip
-$Post_{8c}= post_{8}\shortotimes\ post_{7}\shortotimes\ post_{4}\shortotimes\ post_{456*} 
-= (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_msg}+1+n), \forall n\ge 0$
-\medskip  
-$WI_{8c}(n) = \openrule
+\\Post_{8c}=& post_{8}\shortotimes\ post_{7}\shortotimes\ post_{4}\shortotimes\ post_{456*} 
+= (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_msg}+1+n), \forall n\ge 0\\ 
+WI_{8c}(n) =& \openrule
          {\{\texttt{Q}\mapsto \texttt{q-recv(s\_msg,s\_ec}+n)\}, True, (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_msg}+1+n)}
-         {210 \OTWeakarrow {\nounderline{\texttt{out(s\_msg,s\_ec}+n)}} 202}\forall n\ge 0$
+         {210 \OTWeakarrow {\nounderline{\texttt{out(s\_msg,s\_ec}+n)}} 202}\forall n\ge 0
+\end{align*}
 
@@
 
-\LUDO{il faudrait mieux introduire le paragraphe ci dessous pour expliquer ce qu'il fait ici}
-In practice, we are dealing with finite representations of the (infinite) open automata.
-In \cite{hou:hal-02406098}, we defined a slightly modified definition of the ``coverage'' proof obligation, in the case of strong FH-Bisimulation.
-This modification is required to manage in a finite way all possible instantiations of an OT.
-In the case of weak FH-Bisimulation, the proof obligation from definition \ref{def-Weak-bisim} becomes:
-
- $\forall fv_{OT}. \{ \Pred \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
-  \left[\exists fv_{OT_x}.\\
-    \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
-     \!\land\! \alpha\!=\!\alpha_x\! \land\!  
-     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)\right]\}}$
-
-In which $fv_{OT}$ denotes the set of free variables of all expressions in $OT$.
-
-\medskip
 Our first important result is that Weak FH-bisimilarity is an equivalence in the same way as strong FH-bisimilarity:
@@
 
-\paragraph{Proving bisimulation in practice}
-
+\subsubsection*{Proving bisimulation in practice}
+
+In practice, we are dealing with finite representations of the (infinite) open automata.
+In \cite{hou:hal-02406098}, we defined a slightly modified definition of the ``coverage'' proof obligation, in the case of strong FH-Bisimulation.
+This modification is required to manage in a finite way all possible instantiations of an OT.
+In the case of weak FH-Bisimulation, the proof obligation from definition \ref{def-Weak-bisim} becomes:
+      \begin{multline*}
+\forall fv_{OT}. \Big\{ \Pred \land \Pred_{OT} \implies\\
+ \bigvee_{x\in X}\!
+  \left[\exists fv_{OT_x}.
+    \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
+     \!\land\! \alpha\!=\!\alpha_x\! \land\!  
+     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)\right]\Big\}
+\end{multline*}
+
+In which $fv_{OT}$ denotes the set of free variables of all expressions in $OT$.
 \subsection{Weak bisimulation for open pNets}
@@
 \begin{property}[Non-observability of silent actions]
-The open semantics of a pNets that cannot observe silent actions is an open automaton that  cannot observe silent actions.
+The  semantics of a pNet, as provided in Definition~\ref{def:operationalSemantics}, that cannot observe silent actions is an open automaton that  cannot observe silent actions.
 \end{property}
@@
 
-\begin{definition}[Notation: Semantics of pNets as a weak open automaton]
+\begin{definition}[Semantics of pNets as a weak open automaton]
 Let $A$ be the open automaton expressing the semantics of an open pNet $\pNet$; let $<J,\mathcal{S},s_0, V, \WT>$ be the weak open automaton derived from $A$; this weak open automaton defines the weak semantics of the pNet $\pNet$.
@@
 \end{definition}
+
+From the definition of the weak open automata of pNets, we can now study the properties of weak bisimulation concerning open pNets.
 
@@
 \begin{theorem}[Congruence for  weak bisimulation]\label{weak-thm-congr-eq}
-	Consider an open pNet:
-	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
-	\set{\symb{SV}}\myrangle$ that cannot observe silent actions.
-	Let $j_0\in J$ be a hole. Let $\pNetQ$ and $Q'$ be two weak FH-bisimilar pNets such that 
-	$\Sortop(\pNetQ)=\Sortop(\pNetQ')=\Sort_{j_0}$\footnote{Note that $\Sortop(\pNetQ)=\Sortop(\pNetQ')$ is 
+	Consider an open pNet $P$
+ that cannot observe silent actions, of the form 	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
+	\set{\symb{SV}}\myrangle$.
+	Let $j_0\in J$ be a hole. Let $\pNetQ$ and $Q'$ be two weak FH-bisimilar pNets such that\footnote{Note that $\Sortop(\pNetQ)=\Sortop(\pNetQ')$ is 
 	ensured by 
-	weak bisimilarity.}. Then 
+	weak bisimilarity.} 
+	$\Sortop(\pNetQ)=\Sortop(\pNetQ')=\Sort_{j_0}$. Then 
 	$\pNet[\pNetQ]_{j_0}$ and 
@@
 
-\subsection{Running example}
-In section \ref{sec:weak} we have shown the full satured weak automaton for both the specification and the implementation of the simple protocol.
+\subsubsection*{Running example}
+In Section~\ref{sec:weak} we have shown the full satured weak automaton for both the specification and the implementation of the simple protocol.
 We will show here how we can check if some given relation between these two automata is a weak FH-Bisimulation.
@@
 $j_0$ passes from 
-the set of subnets to the set of holes). 
+the set of sub-pNets to the set of holes). 
 %Then $SV=clone(\alpha_j^{j\in I_k\uplus\{j_0\}\uplus J_k})$.
@@
 
-Now focus on the OTs of the subnets. For each $m\in I_1\uplus I_2$ we have one of the two 
+Now focus on the OTs of the sub-pNets. For each $m\in I_1\uplus I_2$ we have one of the two 
 following OT:\\

### 2020-06-11 2016-Weak-FH-Bisim/AppendixD.tex
updated pNet code in appendix D

--- 2020-05-27 2016-Weak-FH-Bisim/WeakBisim.tex
@@
-% !TEX TS-program = pdflatex
-% !TeX spellcheck = en_GB
-
-\documentclass{lmcs}
-
-\usepackage[T1]{fontenc}
-\usepackage{lmodern}
-%\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
-%\geometry{a4paper}                   % ... or a4paper or a5paper or ...
-%\geometry{landscape}                % Activate for for rotated page geometry
-%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
-\usepackage{graphicx}
-\usepackage{DotArrow}
-\usepackage{hyperref}
-\usepackage{listings}
-\lstset{basicstyle=\small}
-
-%\usepackage{amsfonts}
-%\usepackage{fancyhdr}
-%\usepackage{cite}
-%\usepackage{ifthen}
-%\usepackage{amssymb}
-%\usepackage{fancyhdr}
-%\usepackage{pifont}
-\usepackage{stmaryrd}
-\usepackage{mathtools,mathpartir}
-\usepackage{proof}
-%\usepackage{setspace}
-%\usepackage{indentfirst}
-\usepackage{amsmath,amssymb,amscd,mathrsfs}
-\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
-\usepackage{epsfig,color,subfigure,enumitem,soul}
-\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
-\newcommand{\NOTE}[1]{\textcolor{blue}{\textbf{[NOTE:#1]}}}
-\newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
-\definecolor{darkgreen}{rgb}{0.1, 0.5, 0.1}
-\newcommand{\LUDO}[1]{\textcolor{darkgreen}{#1}}
-\newcommand{\RAB}[1]{\textcolor{magenta}{#1}}
-\newcommand{\coloncolon}{{:\hspace{-.2ex}:}}
-\newcommand{\bigcupdot}{\charfusion[\mathop]{\bigcup}{\cdot}}
-\makeatletter
-\newcommand{\raisemath}[1]{\mathpalette{\raisem@th{#1}}}
-\newcommand{\raisem@th}[3]{\raisebox{#1}{$#2#3$}}
-\makeatother
-\newcommand{\shortotimes}{\!\otimes\!}
-\usepackage{macrospNets}
-
-\newcommand{\nounderline}[1]{#1}
-
-%\usepackage[math]{cellspace}
-%\setlength\cellspacetoplimit{ 37pt}
-%\setlength\cellspacebottomlimit{18pt}
-
-\pagestyle{plain}
-
-% addition to the mathpartir package for red dotted rules,
-% that we use for open-transitions
-
-\newtheorem{theorem}{Theorem}
-%\newtheorem{prop}{Proposition}
-%\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{lemma}{Lemma}
-\newtheorem{algorithm}[theorem]{Algorithm}
-%\newtheorem{remark}[theorem]{Remark}
-\newtheorem{definition}{Definition}
-\newtheorem{property}{Property}
-\newtheorem{example}{Example}
-%\newtheorem{problem}[theorem]{Problem}
-%\newenvironment{proof}{\paragraph{Proof}}{}
-
-\begin{document}
-
-\title{Compositional equivalences based on Open pNets
-%\thanks{This work was partially funded by the Associated Team FM4CPS
-%  between INRIA and ECNU, Shanghai}
-}
-\author{Ludovic Henrio}
-\address{Univ Lyon, EnsL, UCBL, CNRS, Inria,  LIP, F-69342, LYON Cedex 07, France.}
-\email{ludovic.henrio@cnrs.fr}
-
-\author{Eric Madelaine}
-\address{INRIA Sophia Antipolis M\'edit\'erann\'ee, UCA, BP 93, 06902 Sophia Antipolis, France}
-\email{eric.madelaine@inria.fr}
-%\date{}                                           % Activate to display a given date or no date
-\author{Rab\'ea Ameur-Boulifa}
-                          % Activate to display a given date or no date
-
-		%\section{}
-%\subsection{}
-
-\begin{abstract}
-
-Establishing equivalences between programs or system is crucial both for verifying correctness of programs, by establishing that two implementations are equivalent, and for justifying optimisations and program transformations, by establishing that a modified program is equivalent to the source one.
-There exist several equivalence relations for programs, and bisimulations are among the most versatile of these equivalences.
-Among bisimulation relations one distinguishes strong bisimulation, that requires that each action of a program is simulated by a single action of the equivalent program, an weak bisimulations that  is a coarser relations, allowing some of the actions to be
-  invisible or internal moves, and thus not simulated by the equivalent program.
-
-pNets is a generalisation of automata that includes parameters, and hierarchical composition.
-Open pNets are pNets with holes, i.e.
-placeholders inside the hierarchical structure  that can be filled by sub-systems.
-Reasoning on open pNets allows us to reason on open systems.
-  Open pNets have a notion of \emph{synchronised actions}
-  generalizing the usual internal actions (e.g. $\tau$ of CCS, or $i$
-  in Lotos).
-
-This article defines bisimulation relations for the pNet model, to compare  systems described using the pNets model.
- We define a strong bisimulation for open pNets.
-  In practice, as happens in process algebras, strong bisimulation is too strong, and
-  we need to define some coarser relations, taking into account
-  invisible or internal moves.
-  We then define an equivalence relation similar to
-  the classical \emph{weak bisimulation}, and study its properties.
-
-Amon these properties we show compositionality: If two systems are proven equivalent they will be undistinguishable by their context, and they will also be undistinguishable when their holes are filled with equivalent systems.
-
-  Which significant (small) use-case ?
-
-\end{abstract}
-
-\maketitle
-
-\section*{Status and TODO list}
-
-TODOS: AVRIL 2019
-
-- exemple (Eric: failure buffer)
-- biblio (rabea)
-- inuitions de preuves et intuition de bisim de cloture, etc. (Ludo)
-
-%% \TODO{voisr si on redefinit les bigotimes pour prendre des maps et retourner des maps au lieu des substitutions (et on englobe dans une subst a la fin)}
-
-%% \TODO{prendre soin des posts sur les actions partout}
-
-%% ===> dealine 14 Juillet
-
-%% TODOs du 19 decembre
-
-%% - enlever 5.2 et citer avocs
-
-%% - ajouter des proof sketch dans le papier
-
-%% - def 11 point 2:
-%% A, Pred, Post
-%% -----------   in T
-%% s->s'
-%% et A(j)=tau
-%% implies blablabla
-
-%% OLD OLD OLD (check)
-%% Notes de reunion 24 Sept
-
-%% - etat de l art: il faudrait des refs sur bisim en gemneral, probablement avec pas mal de pi calcul (Eric?), des refs sur pourquoi pnets et des refs sur utilite de la weak bisim en verif
-
-%% - target: JLamp
-
-%% Conventions
-%% [14/9/2018]
-
-%% Dans le texte pas de $\backslash$ devant pNet et pLTS
-
-%% pNet devient P ou Q dans les equations; on garde $pLTS$
-
-%% \medskip
-
-%% TODOS et deadline
-
-%% Global and questions:
-%% \begin{itemize}
-%% \item \TODO{should we use iff/implies or LeftRightArrow/Rightarrow}
-%% \item related works
-%% \end{itemize}
-%% Ludo:
-%% \begin{itemize}
-%% \item[X] reorga sec weak bisim + thm -> 10 Juil
-%% \item[X]  intro et orga globale du papier -> fin aout
-%% \item[partial] explication dans semantique open pnets et composition
-%% \item uniformisation pNet P Q
-%% \end{itemize}
-
-\tableofcontents
-
-\section{Introduction}
-
-In the nineties, several 
-works extended the basic behavioural models based on labelled
-transition systems to address value-passing or parameterised systems, using
-various symbolic encodings of the
-transitions~\cite{deSimone85,Larsen87,HennessyLin:TCS95,Linconcur96}. 
-In \cite{Linconcur96}, H.M. Lin addressed value-passing calculi, for which he
-developed a symbolic behavioural semantics, and proved algebraic properties.
-Separately J. Rathke~\cite{HennessyRathke:TCS98} defined another
-symbolic semantics for 
-a parameterised broadcast calculus, together with strong and weak bisimulation
-equivalences, and developed a symbolic model-checker based on a tableau
-method for these processes. 30 years later, no
-practical verification approach and no verification platform are
-using this kind of approaches to provide proof methods for
-value-passing processes or open process expressions.
-
-This article provides a theoretical background that allows us to implement such a verification platform.
-We build upon the concept of pNets that allowed us to give a behavioural semantics of distributed components and verify the correctness of distributed applications in the past 15 years.
-pNets  is a
-low level semantic framework for expressing the behaviour of various
-classes of distributed languages, and as a common internal format for
-our tools.  pNets allow the
-specification of parameterised hierarchical labelled
-transition systems:  labelled transition systems with parameters can be
-combined hierarchically.
-
-We develop here a semantics for a model of interacting processes with parameters and holes. 
-The main interest of our symbolic approach is to define a method to
-prove properties directly on open structures, that will be preserved
-by any correct instantiation of the holes.
-As a consequence, our model allows us to reason on composition
-operators as well as on full-size distributed systems. The parametric
-nature of the model and the properties of compositionability of the
-equivalence relations thus play a major role here and are the main
-strengths of  our contribution.
-
-\subsubsection*{Previous Works and Contribution}
-While most of our previous works relied on closed, fully-instantiated semantics~\cite{BBCHM:article2008,AmeurBoulifa2017,HKM-FASE16}, it is only recently that we could design a first version of a  parameterised semantics for pNets with a strong bisimulation equivalence~\cite{henrio:Forte2016}.
-This article builds open this previous parameterised semantics and provides a cleaner version of the semantics with a slightly simplified formalism, adding a notion of global state to automata.
-The slight simplification of the formula allowed us to adopt a much cleaner presentation where the theory for open automata, the algebra used to define the semantics of pNets with holes, can be studied independently from its application to pNets.
-Also, in \cite{henrio:Forte2016} the study of compositionability was only partial, and in particular the proof that bisimulation is an equivalence is one new contribution of this article and provides a particularly interesting insight on the semantic model we use.
-The new formalism allowed us to extend the work and define weak bisimulation  for open automata, which is entirely new.
-This allows us to define a weak bisimulation equivalence for open pNets with valuable properties of compositionality.
-To summarise, the contribution of this paper are the following
-\begin{itemize}
-\item The definition of open automata: an algebra of parameterised automata with hole with a strong bisimulation equivalence.
-This is an adaptation of~\cite{henrio:Forte2016} with an additional property stating that strong bisimulation equivalence is indeed an equivalence relation.
-\item A semantics for open pNets expressed as translation to open automata. This is an adaptation of~\cite{henrio:Forte2016} with a complete proof that strong bisimulation is compositional.
-\item A theory of weak bisimulation for open automata, and its properties.
-It relies on the definition of weak open transitions that are derived from transitions of the open automaton by concatenating invisible action transitions with one (visible or not) action transition.
-The precise definition of the concatenation is also a major contribution of this article.
-\item A resulting weak bisimulation equivalence for open pNets and a simple static condition on synchronisation vectors inside pNets that is sufficient to ensure that weak bisimulation is compositional.
-\item An illustrative example based on a simple transport protocol, showing the construction of the weak open transitions, and the proof of weak bisimulation.
-\end{itemize}
-
-\subsubsection*{Structure}
-This article is organised as follows. Section~\ref{sec:notations}
-provides the definition of pNets and introduces the notations used in
-this paper, including the definition of open pNets. 
-Section~\ref{sec:OT} defines open automata, i.e. automata
-with parameters and transitions conditioned by the behaviour of
-``holes''; a strong bisimulation equivalence for open automata is also
-presented in this section. 
-Section~\ref{section:op-semantics} gives
-the semantics of open pNets expressed as open automata, and states
-compositional properties on the strong bisimulation for open
-pNets. 
-Section~\ref{sec:weak} defines a weak bisimulation
-equivalence on open automata and derives weak bisimilarity for pNets,
-together with properties on compositionality of weak bisimulaiton for
-open pNets. 
-Finally, Section~\ref{sec:RW} discusses related works and Section~\ref{section:conclusion} concludes the
-paper.
-
-\section{Background and notations}\label{sec:notations}
-This section introduces the notations we will use in this article, and  recalls the definition of pNets~\cite{henrio:Forte2016} with an informal semantics  of the pNet constructs.
-The only significant difference compared to our previous definitions is that we remove here the restriction that was stating that variables should be local to a state of a labelled transition system.
-
-\subsection{Notations}
-%In general $x_i,y_i$ range over variables.
-\subsubsection*{Term algebra.}
-Our models rely on a notion of parameterised actions, that are
-symbolic expressions using data types and variables. As our model aims
-at encoding the low-level behaviour of possibly very different
-programming languages, we do not want to impose one specific algebra
-for denoting actions, nor any specific communication mechanism. So we
-leave unspecified the constructors of the algebra that will allow building
-expressions and actions. Moreover, we use a generic {\em action interaction}
-mechanism, based on (some sort of) unification between two or more action
-expressions, to express various kinds of communication or
-synchronisation mechanisms.
-
-%\def\Talg{\mathcal{T}_{\Sigma}}
-%\def\BoolExprs{\mathcal{B}}
-%\def\Exprs{\mathcal{E}} \TODO{use Exprs}
-%\def\Actionalg{\mathcal{A}}
-
-Formally, we assume the existence of a term algebra $\AlgT$,
-where $\Sigma$ is the signature of the data and action constructors. Within $\AlgT$, we distinguish a set of
- expressions $\AlgE$, including a set of boolean
-expressions $\AlgE$ ($\AlgB\subseteq\AlgE$). We let $e_i$ range over expressions ($e_i\in\AlgE$).
-On top of $\AlgE$ we build the action algebra
-$\AlgA$, with $\AlgA\subseteq\AlgT,
-\AlgE\cap\AlgA=\emptyset$;
-naturally action terms will use data expressions as sub-terms.
-
-Let $a$
-range over action labels, $\symb{op}$ be operators, and $x_i$ and $y_i$ range over
-variable names.
-
-We distinguish two kinds of parameterised actions: one that distinguishes input variables and one that does not. 
-We first define the set of actions that distinguish input variables, they will be used in the definition of \pLTS\ below:
-\[
-\begin{array}[l]{rcl@{\quad}p{5.5cm}}
-  \alpha\in\AlgA&::=&a(p_1,\ldots,p_n)&\text{action terms}\\
-  p_i&::=& ?x~|~e_i&\text{parameters (input variable or expression)}\\
-  e_i&::=& \symb{Value}~|~x~|~\symb{op}(\symb{e}_1,..,\symb{e}_n)&\text{Expressions}
-\end{array}
-\]
-The \emph{input variables} in an action term are those marked with a
-$\symb{?}$.
-We additionally suppose that each input variable does not
-appear somewhere else in the same action term:
-$p_i=?x\Rightarrow\forall j\neq i.\, x\notin \vars(p_j)$
-
-The set of actions that do not distinguish input variables is denoted $\AlgAS$, it will be used in synchronisation vectors of pNets below:
-\[\begin{array}[l]{rcl@{\quad}l}
-  \alpha\in \AlgAS &::=&a(e_1,\ldots,e_n)
-\end{array}
-\]
-
-The function
-$\vars(t)$ identifies the set of variables in a term
-$t\in\AlgT$, and $iv(t)$ returns the name of its input variables (without the '?' marker).
-Action algebras can encode naturally usual point-to-point message passing calculi (using 
-$a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs), but it also allows
-for more general synchronisation mechanisms, like gate negociation in Lotos, or broadcast
-communications.
-
-\subsubsection*{Indexed sets}
-
-In this article, we extensively use indexed structures
-(maps) over some countable indexed sets.   The indices can typically be
-integers, bounded or not.
-We use indexed sets in pNets because we want to consider a set of processes, and specify separately how to synchronise them.
-Roughly this could also be realised using tuples, however indexed sets are more general, can be infinite, and give a compact representation than using the position in a possibly long tuple.
-
-An indexed family is denoted as
-follows: $a_i^{i\in I}$ is a family of elements $a_i$ indexed over the
-set $I$. Such a family
-is equivalent to the mapping $(i\mapsto a_i)^{i\in I}$, and we will also use mapping 
-notations to manipulate indexed sets.
-To specify the set over which the structure is indexed, 
-indexed structures are always denoted with an exponent of the form $i\in I$.
-Consequently, $a_i^{i\in I}$ defines first $I$ the set over which the
-family is indexed, and then $a_i$ the elements of the family.
-
-For example $a^{i\in\{3\}}$ is
-the mapping with a single entry $a$ at index $3$; exceptionally, such mappings with
-only a few entries will also be denoted $(3\mapsto a)$.
-%The operation  $A[j \mapsto a]$ updates the value associated to $j$ in map $A$ so that 
-%it 
-%now corresponds to $a$. 
-When this is not ambiguous, we shall use abusive vocabulary and
-notations for sets, and typically write ``indexed set over I'' when  
-formally we should speak of multisets, and ``$x\in
-A_i^{i\in I}$'' to mean $\exists i\in I.\, x=A_i$.
-%An empty family is denoted $[]$. % (it can be defined as $a_i^{i\in\emptyset}$).
-To simplify equations, an indexed set can be denoted $\set{M}$
-instead of $M_l^{l\in L}$ when $L$ is irrelevant.
-
-$\uplus$ is the disjoint union on sets. We extend it to  disjoint union  of indexed 
-sets defined by the merge of the 
-two sets provided they are indexed on disjoint families.
-The elements
-of the union of two indexed sets are then accessed by using an index of one of the two
-joined families.
-%We suppose here that disjoint unions are always well defined; this
-%requires to choose disjoint  
-%indices in the definition of the component system (e.g. name of
-%methods of different interfaces).
-$\setminus$ is the standard subtraction operation on indexed sets: $\dom(A\setminus B)=\dom(A)\setminus B$.
-
-%%\smallskip\noindent
-%\paragraph*{Indexed sets.}
-%We extensively use indexed structures
-%over some countable indexed sets, which are equivalent to mappings over
-%the countable set. % . The indexes will usually be
-%% integers, bounded or not. Such an indexed family is
-%%denoted
-%%follows:
-%$a_i^{i\in I}$
-%%, or equivalently  $(i\mapsto a_i)^{i\in I}$
-%denotes a family of elements $a_i$ indexed over the
-%set $I$. % Such a family
-%% is equivalent to the mapping $(i\mapsto a_i)^{i\in I}$.
-%% To specify the set over which the structure is indexed,
-%% indexed structures are always denoted with an exponent of the form $i\in I$
-%% (arithmetic only appears in the indexes if necessary).
-%$a_i^{i\in I}$ defines both $I$ the set over which the family is
-%indexed (called \emph{range}), and $a_i$ the elements of the family.
-%E.g., $a^{i\in\{3\}}$ is the mapping with a single entry $a$ at index
-%$3$ ; abbreviated $(3\mapsto a)$ in the following.
-%When this is not
-%ambiguous, we shall use notations for sets, and typically write
-%``indexed set over I'' when formally we should speak of multisets, and
-%write $x\in a_i^{i\in I}$ to mean $\exists i\in I.\, x=a_i$.  An empty
-%family is denoted $\emptyset$. We
-%denote classically with an overline -- $\set{a}$  -- a family when the indexing set 
-%is
-%not meaningful.  $\uplus$ is the disjoint union on
-%indexed sets.
-
-\subsubsection*{Substitutions}
-\label{def:substitutions}
-
-We denote $y\gets e$ a substitution. The application of the substitution is denoted
-$\subst{y\gets e}$, the operation replaces in a term all occurrences 
-of the variable $y$ by the expression $e$. 
-$\Post$ ranges over (indexed) sets of substitutions; $\subst{\Post}$ is the substitution that applies all the substitutions defined by $\Post$ in a parallel manner.
-$\otimes$ is the composition operator on substitutions, such that for any term $t$ we have: $t\subst{\Post\shortotimes\Post'} = (t\subst{\Post'})\subst{\Post}$.
-
-For this property to be valid even if the substitution does not operate on all variables,
-we define the composition operation as follows: 
-%\TODO{version d eric reprise et corrigee}
-%$(x_k\gets e_k)^{k\in K}\shortotimes \Post =  (x_k\gets e_k\subst{\Post})^{k\in K}$
-%\ERIC{J'ai un probleme ici... quand $Post'$ agit sur des vars de $t$ qui ne sont pas substitutees par $Post$, alors les 2 defs de $\shortotimes$ ci-dessus ne sont pas equivalentes:}\\
-%$F(x,z)(\subst{x\gets z}\shortotimes\subst{z\gets 1})=F(x,z)(\subst{x\gets 1})=F(1,z)$\\
-%\ERIC{Alors que}\\
-%$(F(x,z)\subst{x\gets z})\subst{z\gets 1})=F(z,z)\subst{z\gets 1}=F(1,1)$
-%
-%\ERIC{Une definition plus correcte serait peut-etre:}\\
-
-\[(x_{k}\gets e_{k})^{k\in K}\shortotimes (x'_{k'}\gets e'_{k'})^{k'\in K'} =  
-(x_{k}\gets e_{k}\subst{(x'_{k'}\gets e'_{k'})^{k'\in K'}})^{k\in K} \cup (x'_{k'}\gets e'_{k'})^{k'\in K''}\]
-where $K''=\{k'\in K'|x'_{k'}\not\in\{x_k\}^{k\in K}\}$
-%
-%\LUDO{En fait comme on supose qu il y a pas de variable globale et donc que les post doivent affecter toutes les variables ce contre-exemple n est pas applicable!
-apres on peut definir comme ca si on veut ceinture et bretelles mais ca alourdit un peu la definitions}
-%
-%\ERIC{Heu Non... 
-%  En pratique, dans la composition de posts de la regle WT3, les posts assignent bien toutes les variables de leur OT (strong), mais dans la composition, on fini par avoir des trous...
-Voir page 21-22.
-On est tombes tous les deux separemment, Rabea et moi, sur ce genre de cas.}
-% 
-%\LUDO{euuh ca doit etre lie qu fait qu il manque des ec leftarrowec dans les selfloop de l'OA de spec.
-Plutot que changer la def et les preuves je propose de rajouter la condition $vars(s')=dom(Post)$ pour tous les OAs ce qui ne change rien a part pour les selfloop que l on s autorisait apparemment a ecrire en omettant $x:=x$ ...
-au pire l'identite est un post toujours correct et valide}
-
-\subsection{Parameterised Networks (pNets)}
-\label{section:pnets}
-
-pNets are tree-like structures, where the leaves are either \emph{parameterised labelled transition systems (pLTSs)}, expressing the
-behaviour of basic processes, or \emph{holes}, used as placeholders
-for unknown processes. 
-%, of which we only specify the set of possible
-%actions, this set is named the \emph{sort}.
-Nodes of the tree (pNet nodes) are synchronising artefacts, using a
-set of \emph{synchronisation vectors} that express the possible
-synchronisation between the parameterised actions of a subset of the sub-trees.
-
-%\LUDO{introduce magic op}
-%$\CreateISet{a}{i}$ creates a single entry indexed set $(i\mapsto a)$ \emph{but only if 
-%$a$ is not already an indexed set.}
-
-A pLTS is a labelled transition system with variables; variables can be
-used inside states, actions, guards, and
-assignments. 
-%Similarly, to simplify the management of variables and without loss of expressivity, we 
-%suppose that transitions looping to the same state does not do assignments.
-Note that we make no assumption on finiteness of the set of states nor
-on finite branching of the transition relation. Compared to our previous works~\cite{henrio:Forte2016,AmeurBoulifa2017} we extend the expressiveness of the model by making variables global.
-
-\begin{definition}[pLTS]
-\label{pLTS}
-A pLTS is a tuple
-$\pLTS\triangleq\mylangle S,s_0, V, \to\myrangle$ where:
-\begin{itemize}
-\item[$\bullet$]
-$S$ is a set of states.
-\item[$\bullet$]
-$s_0 \in S$ is the initial state.
-%\item[$\bullet$]
- %Variables in
-%$\iv(\alpha)$ are assigned by the action, other variables can be assigned
-%by the additional assignments.
-\item[$\bullet$] $V$ is a set of global variables for the pLTS,
-\item[$\bullet$] $\to \subseteq S \times L \times S$ is the transition relation and 
-$L$ is the set of labels of the form:\\
-$\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in J}\rangle$,
-where $\alpha \in\AlgA$ is a parameterised action, $e_b \in
-\AlgB$ is a guard, and the variables $x_j$ 
-are assigned the expressions $e_j\in \AlgE$.
-If 
-$s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
-		J}\rangle} s'\in \to $ then 
-% REMOVED BECAUSE USELESS: $\iv(\alpha)\!\subseteq\! \vars(s')$, 
-		$\vars(\alpha)\backslash \iv(\alpha)\!\subseteq\! V$, 
-		$\vars(e_b)\!\subseteq\! \vars(s)\cup\vars(\alpha)$, and
-		$\forall j\!\in\! J .\,\left(\vars(e_j)\!\subseteq\! V\cup\iv(\alpha)\land 
-		x_j\!\in V \right)$. %,  and $s= s'\Rightarrow J=\emptyset$.
-
-%\LUDO{I suggest to add: $\{x_j|j\in J\} = \vars(s')$ or $\{x_j|j\in J\} \cup \iv(\alpha)= \vars(s')$} 
-\end{itemize}
-\end{definition}
-
-The semantics of the assignments is that a set of assignments between two states is performed in parallel so that their order do not matter and they all use the values of variables before the transition (or the values received as action parameters).
-
-Now we define
-pNet nodes as constructors for hierarchical behavioural structures.
-A pNet has a set of sub-pNets that can be either pNets or pLTSs, and a
-set of holes, playing the role of process parameters. A pNet is thus a composition operator that can receive processes as parameters; it expresses how the actions of the sub-processes synchronise.
-
-Each sub-pNet exposes
-a set of actions, called \emph{internal actions}. The synchronisation between global actions exposed by the pNet and
-internal actions of its sub-pNets is given by  \emph{synchronisation vectors}: a
-synchronisation vector synchronises one or several internal actions, and
-exposes a single resulting global action.
-
-We now define the structure of pNets, the following definition relies on the definition 
-of holes, leaves and sorts formalised below in Definition~\ref{def-sortholeleave}.
-Informally, holes are process parameters, leaves provide the set of pLTSs at the leaves of the hierarchical structure of a pNet, and sorts give the signature of a pNet, i.e.
-the actions it exposes.
-
-\begin{definition}[pNets]\label{def-pnets}
-A pNet $\pNet$ is a hierarchical structure where leaves are pLTSs and holes:\\
-$\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in 
-K}\myrangle$
-where
-\begin{itemize}
-\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets indexed over $I$. $vars(P_i)$ and $vars(P_j)$ must be disjoint for $i\neq j$.
-%  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which sub-pNets are indexed.
-
-\item[$\bullet$] $J$ is a set of indexes, called \emph{holes}.
-$I$ and $J$ are \emph{disjoint}: $I\!\cap\! J=\emptyset$,  $I\!\cup\! J\neq\emptyset$
-\item[$\bullet$] $\Sort_j \subseteq \AlgAS$  is a set of action terms, denoting the 
-\emph{sort} of
-hole $j$.
-
-\item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
-  synchronisation vectors. $\forall k\!\in\! K,
-  \symb{SV}_k\!=\!\SV{\alpha_{l}^{l\in I_k \uplus J_k}}{\alpha'_k}{e_k}$ where
-  $\alpha'_k\in \AlgAS$, $I_k\subseteq I$, $J_k\subseteq J$,
-  $\forall i\!\in\!
-  I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$,  $\forall j\!\in\!
-  J_k.\,\alpha_{j}\!\in\!\Sort_j$, and $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
-  J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
-$\alpha'_k$. $e_k \in \AlgB$ is a guard associated to the vector such that
-$\vars(e_k)\subseteq \bigcup_{l\in I_k\uplus J_k}{\vars({\alpha_l})}$.
-\end{itemize}
-Synchronisation vectors are identified modulo renaming of variables that appear in their 
-action terms.
-\end{definition}
-
-The preceding definition relies on the auxiliary functions defined below:
-
-\begin{definition}[Sorts, Holes, Leaves, Variables of pNets]\label{def-sortholeleave}~~
-
-  \begin{itemize}
-  \item The sort of a pNet is its signature, i.e. the set of actions in $\AlgAS$ it can
-perform, where each action signature is an action 
-label plus the arity of the action. In the definition of sorts, we do not need to 
-distinguish
-input variables and we remove the
-\emph{input marker} (?) of variables.
-\[
-\begin{array}{l}
-\Sortop(\mylangle S,s_0,V, \to\myrangle) = \{\alpha\subst{?x \gets x| 
-x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
-    J}\rangle} s'\in \to \} \\
-\Sortop(\mylangle \set{\pNet}\!, %\pNet_i^{i\in I}, 
-\set{\Sort},
-\set{\symb{SV}}\myrangle)
-=\{\alpha' |\, \SV{\set{\alpha}}{\alpha'}{e_b}\in\set{\symb{SV}}\}
-\end{array}
-\]
-
-\item The set of variables of a pNet $P$, denoted $vars(P)$ is disjoint union the set of variables of  all pLTSs that compose $P$.
-
-\item
-The set of holes $\Holes(\pNet)$ of a pNet is the indexes of the holes of the pNet 
-itself plus the indexes of all the holes of its subnets.
-It is defined inductively (we suppose those indexes 
-disjoints):
-  \[\begin{array}{l}
-\Holes(\mylangle S,s_0,V, \to\myrangle) \!=\! \emptyset\\
-\Holes(\mylangle \pNet_i^{i\in I}\!,\set{\Sort}, \set{\symb{SV}}\myrangle) 
-=J\uplus{\displaystyle \bigcup_{i\in 
-I}\Holes(\pNet_i)}\\
-\forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
-\forall i_1,i_2\in I.\,i_1\neq i_2\Rightarrow  \Holes(\pNet_{i_1})\cap\Holes(\pNet_{i_2})=\emptyset
-\end{array}\]
-\item
-The set of leaves of a pNet is the set of all pLTSs occurring in the structure, as an 
-indexed family of the form $\Leaves(\pNet)= \mylangle \pNet_i \myrangle^{i \in L}$.
-\[\begin{array}{l}
-\Leaves(\mylangle S,s_0,V, \to\myrangle) \!=\!\emptyset\\%\{\mylangle S,s_0, \to\myrangle\}\\
-\Leaves(\mylangle \pNet_i^{i\in I}\!,%Sort_j^{j\in J}
-\set{\Sort}\!, \set{\symb{SV}}\myrangle) = {\displaystyle \biguplus_{i\in 
-I}\Leaves(\pNet_i)\uplus\{i\mapsto \pNet_i|\pNet_i \text{ is a }\pLTS\}}
-\end{array}\]
-\end{itemize}
-
-A pNet $Q$ is \emph{closed} if it has no hole: $\Holes(Q)=\emptyset$; else it
-is said to be \emph{open}.
-\end{definition}
-
-The informal semantics of pNets is as follows.
-pLTSs behave more or less like  classical automata with conditional branching and variables.
-The actions on the \pLTS s can send or receive values, potentially modifying the value of variables.
-pNets are synchronisation entities: a pNet composes several subnets and  synchronisation vectors define how the subnets interact, where a subnet is either a pNet or a pLTS.
-Synchronisation between subnets is defined by synchronisation vectors that express how an action of a subnet can be synchronised with actions of other subnet, and how the resulting synchronised action is visible to the outside of the pNet.
-Synchronisation vectors also allow to explicitly export an action of a subnet to the next level, or to allow to subnets to synchronise and only exporting a non-observable action (provided such an non-visible action labels exist in the action algebra.
-Finally, a pNet can leave subnets undefined and instead declare holes with a well-defined signature.
-Holes can then be filled with a subnet.
-This is defined as follows.
-
-\begin{definition}[pNet composition]
-	An open pNet: $\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
-	\set{\symb{SV}}\myrangle$
- can be (partially) filled by providing  a pNet $\pNetQ$ of the
-	right sort to fill one of  its holes.	
-	Suppose $j_0\in J$:
-	%% \[\mylangle \pNet_i^{i\in I},S_j^{j\in J}, \symb{SV}_k^{k\in
-	%%   K}\myrangle\left[(\pNet'_i)^{i\in L}\right]= \mylangle \pNet_i^{i\in
-	%%   I}\left[(\pNet'_i)^{i\in L}\right]\uplus(\pNet'_i)^{i\in J\cap L},S_j^{j\in 
-	%%J\setminus L},
-	%% \symb{SV}_k^{k\in K}\myrangle
-	%% \]
-	\[\pNet\left[\pNetQ\right]_{j_0}= \mylangle 
-	\pNet_i^{i\in I}\uplus\{j_0\mapsto \pNetQ\},\Sort_j^{j\in J\setminus \{j_0\}},
-	\set{\symb{SV}}\myrangle
-	\]
-\end{definition}
-
-pNets are composition entities equipped with a rich synchronisation mechanism: synchronisation vectors allow the expression of synchronisation between any number of entities and at the same time the passing of data between processes.
-Their strongest feature is that the data emitted by processes can be used can be used inside the synchronisation vector to do addressing: it is easy to synchronise a process indexed by $n$ with the action $a(v,n)$ of another process.
-This is very convenient to model systems and encode futures or message routing.
-pNets have been used to model GCM distributed component systems, illustrating the expressiveness of the model~\cite{AmeurBoulifa2017}.
-These works show that pNets are convenient to express the behaviour of the system in a compositional way, which is crucial for the definition of the semantics, especially when dealing with a hierarchical component system like GCM.
-Unfortunately, the semantics of pNets and the existing tools at this point were only able to deal with a closed system completely instantiated: pNets could be used as composition operator in the definition of the semantics, which was sufficient to perform finite-state model checking on a closed system, but there was no theory for the use of pNets as operators and no tool for proving properties on open system.
-The semantics of closed pNets~\cite{AmeurBoulifa2017}, defined as an instantiation of labelled transition systems, is not necessary to understand this article but can be useful to  understand the semantics of pNets in a simpler and more operational setting.
-The theory of pNets as operators able to fully take into account open systems is given in the following sections.
-
-\subsection{Running Example}
-To illustrate this work, we use a simple communication protocol, that provides safe transport of data between two processes, over unsafe media.
-
-Figure \ref{SimpleProt:Spec} (left) shows the example principle, which corresponds to the hierarchical structure of a pNet: two unspecified
-processes $P$ and $Q$ (holes) communicate messages, with a data value
-argument, through the two protocol entities.
-Process $P$ sends an $\texttt{p-send(m)}$ message to the $\symb{Sender}$; this communication is denoted as $\texttt{\nounderline{in(m)}}$% , where underline actions represent internal actions that cannot be further synchronised with the environment, similarly to the $\tau$ of CCS.
-In our formalisation we will also denote these actions $\tau$ for simplicity of notations but the examples are easier to read when invisible actions have significant names}
-.
-At the other end, process $Q$ receives the message from the $\symb{Receiver}$.
-The holes $P$ and $Q$ can also have other interactions with their environment, represented here by actions $\texttt{p-a}$ and $\texttt{q-b}$.
-The underlying network is modelled by a medium entity transporting messages from the sender to the receiver, and that is able to detect transport errors and signal them to the sender.
-The return $\symb{ack}$ message from $\symb{Receiver}$ to $\symb{Sender}$ is supposed to be safe.
-The final transmission of the message to the recipient (the hole $Q$) includes the value of the ``error counter'' $ec$.
-
-Figure \ref{SimpleProt:Spec} (right) shows a graphical view of the pNet that specifies the system:
-the full system should be equivalent (e.g.  weakly bisimilar)
-to the two processes connected simply through a perfect medium.  
-The pNet has a tree-like structure.
-The root node of the tree {\it SimpleSystemSpec} is the top level of the pNet structure.
-It acts as the parallel operator.
-It consists of three nodes: two holes $P$ and $Q$ and one subnet, denoted {\it PrefectBuffer}.
-Nodes of the tree are synchronized using four synchronization vectors, that  express the possible synchronizations between the parameterised actions of a subset of the nodes.
-For instance, in the vector "$< \texttt{p-send(m)},\texttt{in(m)},\_> \rightarrow \texttt{\nounderline{in(m)}}$" only $P$ and {\it PrefectBuffer} nodes are involved in the synchronization.
-The synchronization between these processes occurs when  process $P$  performs $\texttt{p-send(m)}$  action sending a message, and  the {\it PrefectBuffer} accepts the message through an $\texttt{in(m)}$ action  at the same time; the result that will be returned at upper level is the action  $\texttt{\nounderline{in(m)}}$.
-
-Figure \ref{SimpleProt:Impl} shows the pNet model of the protocol implementation.
-When the $\symb{Medium}$ detects an error (modelled by a local $\tau$ action), it sends back a $\texttt{m\_error}$ message to the $\symb{Sender}$.
-The $\symb{Sender}$ increments its local error counter $ec$, and resends the message (including $ec$) to the $\symb{Medium}$, that will, eventually, transmit $m,ec$ to the $\symb{Receiver}$.
-%Strictly speaking, as variables are local to each  state, we have two distinct $ec$ variables in the \textit{Sender} pLTS, one in state \texttt{s1}, another one in state \texttt{s2}, the value of the variable is updated along the transitions entering each of the two states.
-
-\begin{figure}[t]
-   \includegraphics[width=.37\textwidth]{XFIG/SimpleProt-Schema}
-   \includegraphics[width=.62\textwidth]{XFIG/SimpleProt2-Spec}
-   \caption{pNet structure of the example and specification expressed as a pNet}
-   \label{SimpleProt:Spec}
-
-\end{figure}
-
-\begin{figure}[t]
-  \centerline{\includegraphics[width=.9\textwidth]{XFIG/SimpleProt2-pNet-tau}}
-  \caption{Composed pNet with the Simple Protocol Implementation}  \label{SimpleProt:Impl}
-\end{figure}
-
-\section{A model of process composition}\label{sec:OT}
-
-The semantics of open pNets will be defined  as an open automaton. An open
-automaton is an automaton where each transition composes transitions of several LTSs with
-action of some holes, the transition occurs if some predicates hold, and can involve a 
-set of state modifications.
-This section defines open automata and a bisimulation theory for them.
-This section can be viewed as an improved version of the formalism described in \cite{henrio:Forte2016}, generalising the automata with a notion of global variable, which makes the state of the automaton more explicit.
-We also adopt a semantics and logical interpretation of the automata that intuitively can be stated as follows: ``if a transition belongs to an open automaton, any refinement of this transition also belongs to the automaton''.
-
-\subsection{Open Automata}
- Open automata (OA) are not composition structures but they are made of transitions that are dependent of the actions of the holes, and they can reason on a set of variables (potentially with only symbolic values).
-%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
-%different 
-%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
-\begin{definition}[Open transitions]\label{def:OT}
-	\label{def:OpenTransitions}
-	An \emph{open transition} (OT) over a
-	set $J$ of holes with sorts $\Sort_j^{j\in J}$, a set $V$ of variables, and a set of states $\mathcal{S}$ is 
-	a structure of the form:	
-	\begin{mathpar}
-	\openrule
-	{	\beta_j^{j\in J'}, \Pred, \Post}
-	{s \OTarrow {\alpha}s'}
-	\end{mathpar}
-	Where $J'\subseteq J$, $s, s'\in\mathcal{S}$ and $\beta_j$
-        is a transition of the hole $j$, with $\beta_j\in\Sort_j$. $\alpha$ is an action 
-        label denoting the resulting action of this open transition.
-%        We call \emph{source variables} of an OT the union of all variables
-%        in the different terms
-%        $\beta_j$ and $\alpha$, and the state variables of $s$.
-        \Pred\ is a predicate over the  variables in $V$ and all variables
-        in the different terms
-       $\beta_j$ and $\alpha$. \Post\ is a set of 
-	assignments that are effective \emph{after the open transition}, they are
-        represented as a substitution of the form $({x_k\gets e_k})^{k\in K}$ 
-	where $\forall k.\, x_k\in V$, and $e_k$ are expressions
-        over the variables $V$ and all variables
-        in the different terms
-       $\beta_j$ and $\alpha$. Because the variables in $V$ can be in both side of the assignments, the assignments are always applied in a parallel manner. Open transitions are identified
-        modulo logical equivalence on their predicate. 
-\end{definition}
-
-It is important to understand the difference between the red dotted rule and a normal 
-inference rule. They correspond to two different logical levels.
-On one side, classical (black) inference rules  use  an expressive logic and are paper rules.
- On the other side, open transition rules (with dotted lines) are logical implications, but using a simple logic (this logic includes the boolean expressions $\AlgB$, boolean operators, and term equality).
-   open transitions could typically be handled in a 
- mechanised way.
-
-An open automaton is  an automaton where each transition is an open transition.
-\begin{definition}[Open automaton]
-	\label{def:open-automaton}
-	An \emph{open automaton} is a structure\\ $A =
-	<J,\mathcal{S},s_0,V,\mathcal{T}>$ where:
-	\begin{itemize}
-		\item[$\bullet$]   $J$ is a  set of indices.
-		\item[$\bullet$]   $\mathcal{S}$ is a set of states and $s_0$ an initial state
-		  among $\mathcal{S}$.
-%       \item[$\bullet$] for each state $s$, $vars(s)=\{v_s\}$ is a set of state variables, 
- \item[$\bullet$] $V$ is a set of variables of the automaton
-		and each $v\in V$ may have an initial value $init(v)$.
-		\item[$\bullet$] $\mathcal{T}$ is a set of open transitions and for each
-		$t\in \mathcal{T}$ there exist  $J'$ with  $J'
-		\subseteq J$, such that $t$ is an open transition over  $J'$
-		and  $\mathcal{S}$.
-
-	\end{itemize}
-
-We take in this article a semantics and logical understanding of these
-automata. Open automata are closed by a simple form of refinement that
-allows us to refine the predicate, or substitute any free variable by
-an expression. More formally, let $\Pred$ be any predicate and $\Post$ any substitution such that $V\cap \dom(\Post)=\emptyset$. Then we have the following
-implication:
-
-	 \begin{mathpar}
-    \openrule
-         {
-           \set{\beta}, \Pred\,',\Post\,'}
-          {t \OTarrow {\alpha} t'}\in\mathcal{T}
-\implies
-    \openrule
-         {
-           \set{\beta}\subst{\Post}, \Pred\,'\subst{\Post}\land\Pred,\Post\shortotimes\Post\,'}
-         {t \OTarrow {\alpha\subst{\Post}} {t'}}\in\mathcal{T}
-\end{mathpar}
-\end{definition}
-
-%\LUDO{I added this paragraph}
-Because of the semantic interpretation of open automata, the set of open transition of an open automaton is infinite (for example because every free variable can be renamed).
-However an open automaton is characterized by a  subset of these open transition which is sufficient to generate, by substitution the other ones.
-In the following, we will abusively write that we define an ``open automaton'' when we provide only the set of open transitions that is sufficient to generate a proper open automaton by saturating each open transition by all possible substitutions and refinements.
-
-Another consequence of the semantics and logical interpretation of the
-formulas is that we make no distinction between the equality and the
-equivalence on boolean formulas, i.e. equivalence of two predicates
-$\Pred$ and $\Pred\,'$ can be denoted $\Pred=\Pred\,'$.
-
-Though the definition is simple, the fact that transitions are complex structures relating events must not be underestimated in order to understand the rest of the article.
-The first element of theory for open automata, i.e.
-the definition of a strong bisimulation, is given below.
-
-\subsection{Bisimulation for open Automata}
-\label{section:bisimulation}
-
-The equivalence we need is a strong bisimulation between
-open automata having exactly the same holes with the same sorts, but using a
-flexible matching 
-between open transitions, this will allow us to compare pNets
-with different architectures.
-
-We define now a bisimulation relation adapted to open automata and their parametric nature.
-The relation relates states of the open automaton and states equivalence between the open transitions between the states.
-Its key characteristics are 1) the introduction of predicates in the bisimulation relation: as states may contain variables, relation between states may depend on the value of the variables; 2) the bisimulation property relates elements of the open transitions and take into account predicates over variables, actions of the holes, and state modifications.
- We name it FH-bisimulation,
- as a short cut for the ``Formal Hypotheses'' over the holes behaviour manipulated in the
- transitions, but also as a reference to the work of De Simone~\cite{deSimone85},
- that pioneered this idea.
-
-A relation over the states of two open automata  $<\!J,\mathcal{S}_1, s_0,V_1,
-   \mathcal{T}_1\!>$ and $<\!J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2\!>$ has the form $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$, it relates states of $\mathcal{S}_1$ and 
-$\mathcal{S}_2$ constrained by a predicate.
-More precisely, for any pair $(s,t)\in \mathcal{S}_1\times \mathcal{S}_2$, there is a 
-   single
-      $(s,t|\Pred_{s,t})\in\mathcal{R}$  stating that $s$ and $t$ are related 
-      if $\Pred_{s,t}$       is 
-      True, i.e. the states are related when the variables in $V_1$ and $V_2$ verify the 
-      predicate $\Pred_{s,t}$. By nature, this is only correctly defines if the variales of the two open automata are disjoint, i.e.  $V_1\cap V_2=\emptyset$.
- FH-bisimulation is defined formally: 
- \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim} ~\\
-\noindent
-\begin{minipage}{0.69\linewidth} 	Suppose that
-   $A_1 = <\!J,\mathcal{S}_1, s_0,V_1,
-   \mathcal{T}_1\!>$ and $A_2 = <\!J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2\!>$
-   are open automata with identical holes of the same sort, with disjoint state variables.
-
- Then 
-$\mathcal{R}$ is an FH-bisimulation if and only if for any  states
-$s\in\mathcal{S}_1$ and $t\in\mathcal{S}_2$, $(s,t|\Pred_{s,t})\in\mathcal{R}$, we 
-have
-the following:
-\end{minipage}
-\hspace{2mm}
-\begin{minipage}{0.30\linewidth}
-	\includegraphics[width=\linewidth]{XFIG/Bisim}
-\end{minipage}
-
- \begin{itemize}
- \item  For any open transition $OT$ in $\mathcal{T}_1$:
- \begin{mathpar}
-     \openrule
-         {
-           \beta_j^{j\in J'},\Pred_{OT},\Post_{OT}}
-         {s \OTarrow {\alpha} s'}
-
-\end{mathpar}
- there exist   open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
- \begin{mathpar}
-%    \left( fresh \ \set{\alpha_i}, \set{b_j}, v_x.\ \
-    \openrule
-         {
-           \beta_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {t \OTarrow {\alpha_x} t_x}
-%         \right)
-\end{mathpar}
- such that  $\forall x, J'=J_{x}$ and there exists $\Pred_{s',t_x}$ such that $(s',t_x|\Pred_{s',t_x})\in 
- \mathcal{R}$
- and  \\
- $\Pred_{s,t} \land \Pred_{OT}\implies$\\
-%\hspace{1cm}
- $\displaystyle{\bigvee_{x\in X}
-   \left( \forall j. \beta_j=\beta_{jx}  \land \Pred_{OT_x}
-     \land \alpha\!=\!\alpha_x \land  
-     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}$
-     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
-     %     \right)$.
-%\bigskip
-%
-% $\Pred_{s,t} \land \Pred_{OT}\implies\bigvee_{x\in X} \Pred_x$
-%and\\
-%%\hspace{1cm}
-% $ \forall{x\in X}. \Pred_x \land \Pred_{s,t} \land \Pred_{OT} \Rightarrow
-%   \left( \forall j. \beta_j=\beta_{jx}  \land \Pred_{OT_x}
-%     \land \alpha\!=\!\alpha_x \land  
-%     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)$
-%     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
-%     %     \right)$.
-
-%     \TODO{Eric: j'ai ajoute $\exists$ sur les predicats $\Pred_{s',t_x}$, qui n'etaient pas definis...}
-
- \item  and symmetrically any open transition from $t$ in $\mathcal{T}_2$ can be 
-      covered by a set of transitions from $s$ in $\mathcal{T}_1$.
- \end{itemize}
-
-% \TODO{Eric: il reste des petits bugs genre $s^{2'}_x$ plutot que
-%   $s^{2}_x$}
-
-%Where $\symb{Subst}(\Pred,\Post)$ is the parallel substitution of all
-%assigned variables.
-
-% \TODO{do we want formulas for this?}
- \end{definition}
-Classically, $\Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}$
-applies in parallel the  
-substitutions $\Post_{OT}$ and $\Post_{OT_x}$ (parallelism is crucial
-inside each $\Post$ set but not between  $\Post_{OT}$ and
-$\Post_{OT_x}$ that are independent), applying the assignments of the involved rules.
-We can prove that such a bisimulation is an equivalence relation.
-
-\begin{theorem}[FH-Bisimulation is an equivalence]\label{thm-equiv} Suppose $\mathcal{R}$ 
-is an FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
-reflexive, symmetric and transitive.
-\end{theorem}
-
-The proof of this theorem can be found in Annex~\ref{thm-equiv-proof}. The
-only non-trivial part of the proof is the proof of transitivity. It
-relies on the following elements. First,  the transitive composition
-of two relations with predicate is defined; this is not exactly
-standard as it requires to define the right predicate for the
-transitive composition and producing a single predicate to relate any
-two states. Then the fact that one open transition is simulated by a
-family of open transitions leads to a doubly indexed family of
-simulating open transition; this needs particular care, also because
-of the use of renaming (\Post) when proving that the predicates
-satisfy the definition (property on $\Pred_{s,t} \land \Pred_{OT}$ in
-the definition).
-
-%\TODO{have a look at the end of the sec}
-
-\medskip
-
-\subsubsection*{Note on finite versus infinite open automata:} 
-As mentioned in Definition \pageref{def:open-automaton}, we adopt here a semantic view on open automata. More precisely, in \cite{hou:hal-02406098}, we formerly define
-\emph{semantic open automata} (infinite as in Definition \ref{def:open-automaton}),
-and \emph{structural open automata} (finite) that can be generated as
-the semantics of pNets (see Definition \ref{def:operationalSemantics}), and used in the implementation. Then we define
-an alternative version of our bisimulation, called
-structural-FH-Bisimulation, based on structural open automata, and
-prove that the \emph{semantic} and \emph{structural} FH-Bisimulations coincide.
-In the sequel, all mentions of finite automata, and algorithms for
-bisimulations, implicitly refer to their \emph{structural} versions.
-
-If we assume that everything is finite (states and transitions in the
-open automata, and the predicates in $\mathcal{R}$, then it is easy to
-prove that it is decidable whether a relation is a 
-FH-bisimulation, provided the logic of the predicates is
-decidable (proof in \cite{henrio:Forte2016}). Formally:
-
-\begin{theorem}[Decidability of FH-bisimulation]
-Let $A_1$ and $A_2$ be finite open automata
-and $\mathcal{R}$ a relation over their states $\mathcal{S}_1$ and
-$\mathcal{S}_2$ constrained by a finite set of predicates. Assume that
-the predicates inclusion is decidable over  
-the action algebra $\AlgA$. Then it is decidable whether the relation 
-$\mathcal{R}$ is a FH-bisimulation.
-
-\end{theorem}
-
-\section{Semantics of Open pNets}
-\label{section:op-semantics}
-
-This section defines the semantics of an open pNet as a translation into an open automaton. 
-In this translation, the states of the open automata are obtained from
-the states of the pLTSs at the leaves of the composition. The
-predicates on the transitions are obtained both from the predicates on
-the pLTSs transitions and from the synchronisation vectors involved in
-the transition.
-
-The definition of bisimulation for open automata allows us to derive a
-bisimulation theory for open pNets. As pNets are composition
-structures, it then makes sense to prove composition lemmas: we prove
-that the composition of strongly bisimilar pNets are themselves
-bisimilar.
-
-\subsection{Deriving an open automaton from an open pNet}
-To derive an open automaton from a pNet, we need to describe the set of states of the automaton, and then we will detail the construction rule for transitions of the automaton, this will rely on the derivation of predicate unifying synchronisation vectors and the actions of the pNets involved in a given synchronisation.
-
-%Then the semantics of a pNet is characterized by a set of {\em open
-%transitions}, where the hypotheses on process parameters are
-%replaced by 1) transitions of the pLTSs at the leaves, and 2) formal
-%hypotheses on the transitions of the holes. A {\em predicate} is used
-%to relate the parameters and names appearing in the actions of the
-%leaves and the holes involved in the rules, but also appearing in  the resulting action.
-
-We first define states of open pNets as tuples of states. We denote them
- as $\triangleleft\ldots\triangleright$ for distinguishing tuple 
-states from other tuples.
-\begin{definition}[States of open pNets]\label{def-states}
-  A state of an open pNet is a tuple (not necessarily finite) of the
-  states of its leaves.
-
-  For any pNet \pNet, let $\Leaves(\pNet) = \mylangle S_i,{s_i}_0,V, \to_i\myrangle^{i \in L}$ be 
-  the set of pLTS at its leaves,
-  then $States(\pNet) = \{\triangleleft s_i^{i\in L}
-  \triangleright| \forall i\in L. s_i \in S_i\}$.
-A pLTS being its own single leave:\\
-  $States(\mylangle S,s_0,V, \to\myrangle) = \{\triangleleft s \triangleright| s \in S, \}$.  
-%This could be encoded as a mapping from variables of the pNet to expressions, of the form: $\sigma=\{x_i\to e_i\}^{i\in I},\,(x_i\in vars(S))$.
-%\LUDO{j ai ajoute les variables mais c est pas tres beau}
-
-The initial state is defined as:
-$InitState(\pNet) = \triangleleft {{s_i}_0}^{i\in L}  \triangleright$.
-\end{definition}
-To be precise, the state of each pLTS is entirely characterised by both the state of the automaton, and the value of its variables $V$.
-Consequently, the complete characterization of the state of a pNet should take into account the value of its variables $vars(P)$.
-
-%% \begin{example} \emph{State of a pNet}
-%%   The states of pNet \texttt{EnableCompL} are:
-%%   $\triangleleft 00 \triangleright, \triangleleft 10 \triangleright, \triangleleft 11 \triangleright$
-%% \end{example}
-
-\paragraph{\hl{Predicates:}} 
-%Let
-%$\mylangle\set{\pNet},\set{\Sort},\set{\symb{SV}}\myrangle$
-%be a pNet. 
-Consider a synchronisation vector $\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
-{\alpha'} 
-{e_b}$. We 
-define a
-predicate $\Predsv$ relating
-the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
-\[\begin{array}{l}\Predsv \Big(\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
-{\alpha'} 
-{e_b}, \alpha_i^{i\in I}, \beta_j^{j\in J}, \alpha\Big)\Leftrightarrow \\~\qquad\qquad%\bigg(
-%
-%\exists {(\alpha'_i)}^{i\in I},
-%{(\beta'_j)}^{j\in J},v'.\, SV=
-%\\~~\land
-\forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, \beta_j=\beta'_j \land 
-\alpha=\alpha' 
-\land e_b
-\end{array} 
-%\bigg)
-\]
-
-Somehow, this predicate entails a verification of satisfiability in the sense that if the 
-predicate $\Predsv$ is not satisfiable, then the transition associated with the 
-synchronisation will not occur in the considered state, or will occur with a \False\ precondition which is equivalent.
-If the action families do not match or if there is no valuation of
-variables such that the above formula can be ensured then the predicate is undefined.
-
-The definition of this predicate is not constructive but it is easy to build the predicate constructively by brute-force unification of the sub-pNets actions with the corresponding vector actions, possibly followed by a simplification step.
-
-%\TODO{Eric: rewrite example with new Protocolkeep only OT1, and adapt comments}
-\begin{example}[\hl{An open-transition}]
-  \label{OT:SimpleProt}
-At the upper level, the $\symb{SimpleSystem}$ pNet of Figure \ref{SimpleProt:Impl} has 2 holes and $\symb{SimpleProtocol}$ as
-a subnet, itself containing 3 pLTSs. One of its possible open transitions
-(synchronizing the hole $P$
-with the $\symb{Sender}$ within the \emph{SimpleProtocol}) is:
-
- \smallskip\noindent
- \[  OT_1  = \openrule{
-      \{\texttt{P}\mapsto \texttt{p-send(m)}\},  [\texttt{m=m'}],
-        (\texttt{s\_msg}\gets \texttt{m})
-                      }
-    {\ostate{s_0,m_0,r_0} \OTarrow{\nounderline{\texttt{in(m')}}} \ostate{s_1,m_0,r_0}}
-    \]
-
-    \smallskip
-    The global states here are triples, build as the product of states of the 3 pLTSs (remember the holes have no state). The assignment
-    $Post$ uses the variable $\texttt{m}$ from the action of hole $\texttt{P}$ to set the
-    value of the sender variable named $\texttt{s\_msg}$.
-
- %%  The \emph{SimpleProtocol} pNet of Fig. \ref{SimpleProt:Spec} has 3 controllers and no holes. One of its possible open-transition (the sender sending $(m)$ to the medium) is:
-
- %% \smallskip\noindent
- %% $  OT_2  = \openrule{
- %%   \emptyset; Pred=[send(SV\_m)=send(s_\_m);in(SV\_m)=in(?m)];  \\ Post=\{m_\_m:=?m\}
- %%                      }
- %%    {\ostate{s_1,m_0,r_0} \OTarrow{\nounderline{send(SV\_m)}} \ostate{s_2,m_1,r_0}}
- %%    $
-
- %%    That can be simplified to:
-
- %%    \ERIC{Apres application des substitutions et simplification du predicat:}
-
- %%     $  OT_2  = \openrule{
- %%      \emptyset; Pred=\True;  \\ Post=\{m_\_m:=s_\_m\}
- %%                      }
- %%    {\ostate{s_1,m_0,r_0} \OTarrow{\nounderline{send(s_\_m)}} \ostate{s_2,m_1,r_0}}
- %%    $
-
- %%    \smallskip
- %%    Note that the global states shows how the sender and the
- %%    first medium have evolved during this transition, the sender
- %%    moving from $s_1$ to $s_2$, and the first (forward) medium from
- %%    $m_0$ to $m_1$.
- %%    The predicate $Pred$ involves the state variables $s_\_m$ and
- %%    $s_\_sb$ of the sender, while the assignment $Post$ sets the
- %%    state variables of the medium.
-
-    \smallskip
-
-\end{example}
-
-We build the semantics of open pNets as an open automaton over the states  given by 
-Definition~\ref{def-states}. The open transitions first
- project the global state into states of the leaves, then apply
-pLTS transitions on these states, and compose them with the sort of the holes. %The pNet
-%structure does not appear in the open-automaton, only the
-%set of Holes and the set of Leaves.
-The semantics    instantiates fresh variables using the predicate $\fresh(x)$, additionally, for an action 
-$\alpha$, $\fresh(\alpha)$ means all variables in $\alpha$ are fresh.
-
-\begin{definition}[Semantics of open pNets]
-	\label{def:operationalSemantics} The semantics of a pNet $\pNet$ is an open automaton $A\!= 
-	<\!\!Holes(\pNet),States(\pNet),InitState(\pNet),vars(P),\mathcal{T}\!\!>$ where $\mathcal{T}$   is the smallest set of open transitions such that $\mathcal{T}=\{OT\,|\,\pNet \models OT \}$ and	$\pNet \models OT$	is defined by the following  rules:
-%	\begin{itemize}
-%		\item $J$ is the set of holes: $Holes(p)= J$. 
-		%  \item $\set{L}^L = Leaves(p), \set{H}^J = Holes(p)$
-%		\item ${\mathcal{S}} = States(p)$ and $s_0 = InitState(p)$
-%		\item $\mathcal{T}$ is the smallest set of open transitions		satisfying the rules below:
-%	\end{itemize}
-
-	%% \TODO{ We should be careful here: after (re) reading "Huimin
-	%% 	Lin, 'Symbolic Transition Systems with Assignements', Concur'96" I
-	%% 	think handling assignments is not trivial, even for comparisons of pLTSs. }
-
-\begin{itemize}
-\item The rule for a pLTS  checks that the guard is verified and transforms assignments into post-conditions:		
-\begin{mathpar}\inferrule
-		{ s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
-					J}\rangle} s'\in \to  }
-		{ \mylangle  S,s_0, \to \myrangle
-			\models
-			\openrule
-			{\emptyset ,
-			e_b,\left\{x_j\gets e_j\right\}^{j\in J}}
-			{\ostate{s} \OTarrow{\alpha} \ostate{s'}}
-		}\quad {\TrUn}
-\end{mathpar}
-%	Note that this note is greatly simplified by the fact that variables are local to 
-%	thread; introducing global state variables or accepting loops to the same 
-%	state would 
-%	require to reason 
-%	on the scope of 
-%	each variables, and to introduce additional variables to handle the several occurence 
-%	of the same pLTS variable in the predicates. Indeed the constraints on pLTS 
-%	transitions 
-%	ensure that the same variable never appears both on the left and on the right of the 
-%	equations of a predicate.
-
-\item	The second rule deals with pNet nodes: for each possible
-	synchronisation vector (of index $k$) applicable to the rule subject, the premisses
-	include one {\em open transition} for each sub-pNet involved, one possible
-	{\em action} for each hole involved, and the predicate relating these
-	with the resulting action of the vector. The sub-pNets involved are split between two 
-	sets, $I_2$ for subnets that are pLTSs, and $I_1$ for the others, $J$ is the set of 
-	holes involved in the transition\footnote{Formally, if $SV_k \!=\! \SV{({\alpha'})_m^{m 
-	\in M}}{\alpha'}{e_b}$ is a synchronisation vector  of \pNet\  then $J=M\cap 
-	\Holes(\pNet)$, $I_2=M\cap \Leaves(\pNet)$,  $I_1=M\setminus J \setminus 
-	I_2$}.                                                                    
-\begin{mathpar}
-    \mprset {vskip=.8ex}
-\inferrule
-    {
-\Leaves(\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in 
-    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
-k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
-\\
-\\     	
-	\forall m\!\!\in\!\! I_1. {\pNet_m 
-	\models\openrule
-    	{
-    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
-    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
-    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
-  \qquad
-\forall m\!\!\in\!\! I_2.		{ \pNet_m 
-    	 \models
-    	\openrule
-    	{\emptyset, \Pred_m, \Post_m}
-    	{\ostate{s_m} \OTarrow {\alpha_m}
-    		\ostate{s_m'}} }\\\\
-    J' = \biguplus_{m\in I_1}\!\! J_m \uplus J	\\
-    	\Pred = \bigwedge_{m\in I_1\uplus I_2}\!\! \Pred_m \land
-    	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2},\beta_j^{j\in J},\alpha)\\ 
-    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
-    \fresh(\alpha'_m,\alpha',\beta_j^{j\in J},\alpha) 
-    }
-    {\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
-    	\models
-    	{\openrule
-    		{
-    		\beta_j^{j\in J^\prime}, \Pred,  \biguplus_{m\in I_1\uplus I_2} 
-    		\Post_m}
-    		{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
-    			\ostate{(s_i^\prime)^{i\in L}}}
-    	}
-    }\quad {\TrDeux}
-\end{mathpar} 
-\end{itemize} 
-	\medskip
-%        \TODO{may be explain how $\Pred(SV,a_i^{i\in I_k},b_j^{j\in
-%            J_k},v)$ is built ? You mean more than what is written on previous page????}
-	%%    \TODO{I have tentatively added the sort constraint on hole actions, that was
-	%%not included in the first version... I'm unsure whether this is the best place to
-	%%include it, because it may change the decidability conditions on predicates}
-\end{definition}
-        	A key to understand this rule is that the open transitions are
-	expressed in terms of the leaves and holes of the pNet structure,
-	i.e. a flatten view of the pNet, e.g. $L$ is the index set of the
-	Leaves, $L_m$ the index set of the leaves of one subnet indexed $m$, so all $L_m$
-	are disjoint subsets of $L$. Thus the states in the open transitions,
-	at each level, are tuples including states of all the
-	leaves of the pNet, not only those involved in the chosen
-	synchronisation vector.
-
-Note that  the construction is symbolic, and each open-transition deduced expresses a whole family of
-behaviours, for any possible value of the variables.
-%
-
-In \cite{henrio:Forte2016}, we have shown a detailed example of the construction of a complex open transition, building a deduction tree using rules \TrUn ~and \TrDeux.
-
-We have shown in \cite{henrio:Forte2016} that an open pNet
-with finite synchronisation sets, finitely many leaves and
-holes, and each pLTS at leaves having a finite number of states and
-(symbolic) transitions, has a finite automaton. The algorithm for building such an automaton can be found in~\cite{QBMZ-AVOCS18}.
-
-%% \subsection{Post-processing: Elimination of intermediate variables}
-
-%% While building the open transitions, many new variable names are
-%% created, as fresh local variables of synchronisation vectors, and
-%% fresh result variables of intermediate OTs. While these are required
-%% for the semantic construction, they are not significant in the
-%% resulting open automaton. In fact they carry information on the
-%% internal structure of the pNet system, and this information should
-%% \_not\_ be visible when looking at the system as a black box, and in
-%% particular when comparing its behaviour with another system, e.g. by
-%% bisimulation.
-
-%% In the resulting predicate the only significant variables are :\\
-%% - the input variables of pLTS transitions \TODO{heu, non, meme pas, si
-%%   ce sont des comm internes!}\\
-%% - the actions of holes\\
-%% - the result action at toplevel.
-
-%% So we transform the predicates of the resulting OTs, eliminating all
-%% intermediate variables. \TODO{Explain why this should work !! Maybe
-%%   need to be more precise on unification in the matching...}
-
-%\TODO{Eric: full (???) result of the tool execution on the running example on the Simple Prot Spec: Done, on the Counetr version !}
-
-%\begin{figure}[ht]
-%   \centerline{\includegraphics[width=11cm]{ATG/SPSpecOpen}}
-%   \caption{Specification OA}
-%   \label{SimpleProtCounter:SpecOA}
-%\end{figure}
-
-\begin{figure}[ht]
-   \centerline{\includegraphics[width=13cm]{XFIG/SPSpecOpen}}
-   \caption{Specification Open Automaton}
-   \label{SimpleProtCounter:SpecOA}
-\end{figure}
-
-\subsection*{Example}  Figure~\ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the Specification pNet given in Figure \ref{SimpleProt:Spec}. 
-For later references, we give to the transitions of this (strong)
-Specification automaton as $SS_i$ while transitions of the
-Implementation automaton will be labelled $SI_i$. In the figure we
-have annotated each global state with the set of corresponding pLTS variables.
-
- \begin{figure}[ht]
-  \centerline{\includegraphics[width=15cm]{XFIG/SPImplOpen}}
-  \caption{Open Automaton of the Simple Protocol Implementation}  \label{SimpleProtCounter:ImplOA}
-\end{figure}
-
-    Figure \ref{SimpleProtCounter:ImplOA} shows the open automaton of the implementation $SimpleSystem$ (Figure \ref{SimpleProt:Impl}).
-In this drawing, we have short labels for states, representing $\ostate{s_0,m_0,r_0}$ by \texttt{000}.
-Note that open transitions are denoted $\texttt{SI}_i$ and tau open transition by  $\texttt{SI}_{\tau}$.
-The resulting behaviour is quite simple:  we have a main loop including receiving a message from $P$ and transmitting the same message to $Q$, with some intermediate $\tau$ actions from the internal communications between the protocol processes.
-In most of the transitions, you can observe that data is propagated between the successive state variables (holding the message, and the error counter value).
-On the right of the figure, you have a loop of $\tau$ actions ($\texttt{SI}_4$, $\texttt{SI}_5$ and $\texttt{SI}_6$)  showing the handling of errors and corresponding increments of the error counter.
-
-\subsection{pNet Composition Properties: composition of open transitions}
-The semantics of open pNets allows us to prove two crucial properties relating pNet composition with pNet semantics: open transition of a composed pNet can be decomposed into open transitions of its composing sub-pNets, and conversely, from the open transitions of sub-pNets,  an open transition of the composed pNet can be built.
-
-We start with decomposition: from one open transition of $P[Q]_{j_0}$, we exhibit 
-corresponding behaviours of $P$ and $Q$, and determine the relation between their 
-predicates:
-\begin{lemma}[Open transition decomposition\label{lem-decompose}] Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$}.
-	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose:
-	\[ P[Q]_{j_0}  
-		\models
-		{\openrule
-			{
-				\beta_j^{j\in J}, \Pred,  
-				\Post}
-			{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
-				\ostate{s_i'^{\, i\in L}}}
-		}
-	\]
-		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.
-		 Then there exist $\alpha_Q$, $\Pred\,'$, $\Pred\,''$, 
-		$\Post\,'$, $\Post\,''$ s.t.:\\[-2ex]
-		%\[
-		\begin{mathpar}
-		P\models{\openrule
-			{
-				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
-				\Pred\,',  
-				\Post\,'}
-			{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {\alpha}
-				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
-		}%\]
-	\vspace{-2.2ex}\\\text{and~~}
-		%\[
-		Q\models{\openrule
-			{
-				\beta_j^{j\in J\cap\Holes(Q)}, \Pred\,'',  
-				\Post\,''}
-			{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
-				\ostate{s_i'^{\,i\in L_Q}}}
-		}%\]
-		\end{mathpar}
-		and  $\Pred \iff \Pred\,'
-		\land \Pred\,''\land \alpha_Q=\beta_{j_0}$, $\Post=\Post\,'\uplus 
-		\Post\,''$ where $\Post\,''$ is the restriction of $\Post$ over variables of 
-		$Q$.
-\end{lemma}
-
-Lemma \ref{lem-compose} is combining an open transition of $P$ with
-an open transition of $Q$, and building a corresponding transition of
-$P[Q]_{j_0}$, assembling their predicates.
-
-\begin{lemma}[Open transition composition]\label{lem-compose} 
-	Suppose $j_0\in J$ and:\\[-2ex]
-\begin{mathpar}
-%\[
-P\models{\openrule
-	{
-		\beta_j^{j\in J}, 
-		\Pred,  
-		\Post}
-	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
-		\ostate{s_i'^{\, i\in L}}}
-}%\]
-\text{~~and~~}
-%\[
-Q\models{\openrule
-	{
-		\beta_j^{j\in J_Q},
-		 \Pred\,',  
-		\Post\,'}
-	{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
-		\ostate{s_i'^{\, i\in L_Q}}}
-}%\]
-\end{mathpar}
-Then, we have\\[-2ex]
-	\[ P[Q]_{j_0}  
-	\models
-	{\openrule
-		{
-			\beta_j^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
-			\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0},  
-			\Post\uplus \Post\,'}
-		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {\alpha}
-			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
-	}
-	\]
-\end{lemma}
-
-Note that this does not mean that any two pNets can be composed and produce an open 
-transition. Indeed, the predicate $\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0}$ is often not  satisfiable, in particular if the action  $\alpha_Q$ cannot be matched with $\beta_{j_0}$.
-Note also that $\beta_{j_0}$ is  only used as an intermediate term inside formulas in the composed open transition: it 
-does not appear neither as global action nor as an action of a hole.
-
-\subsection{Bisimulation for open pNets -- a composable bisimulation theory}
-\label{section:bisimulation-PN}
-As  our symbolic operational semantics provides an open automaton, we can apply the notion of
-	strong (symbolic) bisimulation on automata to open pNets:
-\begin{definition}[FH-bisimulation for open pNets]\label{def:bisim-pnets}
-Two pNets are FH-bisimilar if there exists a relation between their associated 
-automata that is an FH-bisimulation and their initial states are in the relation (i.e. the predicate associated with the initial states is verifiable).
-%\TODO{check}
-\end{definition}
-%\TODO{Predicate=True me pose un probleme...
-typiquement, on a besoin d'une ``condition initiale'', pour avoir des pNets data-oriented equivalents a leur version state-oriebted => remove the constraint}
-
-We can now prove that pNet composition  preserves
-FH-bisimulation. More precisely, one can define two preservation
-properties, namely 1) when one hole of a pNet is filled by two bisimilar other (open) pNets; and 2) when the same hole in two bisimilar pNets are
-filled by the same pNet, in other words, composing a pNet with two
-bisimilar contexts. The general case will be obtained by
-transitivity of the bisimulation relation (Theorem~\ref{thm-equiv}).
-
-\begin{theorem}[Congruence]\label{thm-congr-eq}
-	Consider an open pNet:
-	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
-	\set{\symb{SV}}\myrangle$.
-	Let $j_0\in J$ be a hole. Let $\pNetQ$ and $\pNetQ'$ be two FH-bisimilar pNets such that 
-	$\Sortop(\pNetQ)=\Sortop(\pNetQ')=\Sort_{j_0}$\footnote{Note that $\Sortop(\pNetQ)=\Sortop(\pNetQ')$ is 
-	ensured by 
-	strong bisimilarity.}. Then 
-	$\pNet[\pNetQ]_{j_0}$ and 
-	$\pNet[\pNetQ']_{j_0}$ are FH-bisimilar.
-\end{theorem}
-
-\begin{theorem}[Context equivalence]\label{thm-ctxt-eq}
-	Consider two FH-bisimilar open pNets:
-	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
-	\set{\symb{SV}}\myrangle$ and 	$\pNet' = \mylangle {\pNet'}_i^{i\in I}, 
-	\Sort_j^{j\in 
-	J}, 	\set{\symb{SV'}}\myrangle$ 
-	(recall they must have the same holes to be bisimilar).
-	Let $j_0\in J$ be a hole, and $Q$ be a pNet such that $\Sortop(Q)=\Sort_{j_0}$. Then 
-	$\pNet[Q]_{j_0}$ and 
-	$\pNet'[Q]_{j_0}$ are FH-bisimilar.
-\end{theorem}
-
-Finally, the previous theorems can be composed to state a general theorem about 
-composability and FH-bisimilarity.
-\begin{theorem}[Composability] \label{thm-composability}
-	Consider two FH-bisimilar pNets with an arbitrary number of holes, when replacing, 
-	inside those two original pNets, a subset of the holes by FH-bisimilar pNets, we 
-	obtain two FH-bisimilar pNets.
-\end{theorem}
-This theorem is quite powerful.
-It somehow implies that the theory of open pNets is convenient to study properties of process composition.
-Open pNets can indeed be used to study process operators and process algebras, as shown in~\cite{henrio:Forte2016}, or to study interaction protocols~\cite{BHHM:FACS11}.
-
-\section{Weak bisimulation}\label{sec:weak}
-
-Weak symbolic bisimulation was introduced to relate transition systems
-that have indistinguishable behaviour, with respect to some definition
-of \emph{internal actions} that are considered local to some
-subsystem, and consequently cannot be observed, nor used for
-synchronisation with their context.
-The notion of non-observable actions varies in different contexts,
-e.g. $tau$ in CCS, and $i$ in Lotos, we could define classically a set of
-\emph{internal/non-observable actions} depending on a specific action
-algebra. In this paper, to simplify the notations, we will simply use $\tau$ as the single non-observable action; the generalisation of our results to a set of non-observable actions is trivial. 
-Naturally, a non-observable action cannot be synchronised with
-actions of other systems in its environment. 
-We show here that under such assumption of non-observability of $\tau$ actions, see Definition~\ref{def:Non-ObsTau}, we can define a weak bisimulation relation that is compositional, in the sense of open pNet composition.
-In this section we will first define a notion of weak open transition similar to open transition.
-In fact a weak open transition is made of several open transitions labelled as non-observable transitions, plus potentially one observable open transition.
-This allows us to define weak open automata, and a weak bisimulation relation based on these weak open automata.
-Finally, we apply this weak bisimulation to open pNets, obtain a weak bisimilarity relationship for open pNets, and prove that this relation has compositional properties.
-
-%% \TODO{we should understand if it make sense to distinguish invisible
-%%   from synchronised actions: in the Forte paper we wrote ``using  as 
-%% \emph{invisible actions} a subset of the
-%% \emph{synchronised actions} defined in Section~\ref{section:pnets}''}.
-
-%% Proving bisimulation properties on our hierarchical broadcast example
-%% would take too much space for this paper. Moreover, interesting
-%% properties of the HB example would rather be adequate for weak
-%% bisimulation, and its large state-space would require some
-%% tool-assistance, both for the generation of the open-automata and for
-%% their comparison.
-
-\subsection{Preliminary definitions and notations}
-
-We first specify in terms of open transition, what it means for an action to be non-observable.
-Namely, we constraint ourselves to system where the emission of a $\tau$ action by a sub-pNet cannot be observed by the surrounding pNets.
-In other words, a pNet cannot change its state, or emit a specific observable action when one of its holes emits a $\tau$ action.
-
-More precisely, we state that $\tau$ is not observable if the automaton always allows any $\tau$ transition from holes, and additionally the global transition resulting from a $\tau$ action of a hole is a $\tau$ transition not changing the pNet's state.
-We define $\Id(V)$ as the identity function on variables of $V$.
-\begin{definition}[Non-observability of $\tau$ actions]\label{def:Non-ObsTau}
-An open automaton $A = <J,\mathcal{S},s_0,V,\mathcal{T}>$ \emph{cannot observe $\tau$ actions} if and only if for all $j$ in $J$ and $s$ in $\mathcal{S}$ we have:
-\begin{enumerate}
-\item
-\[ \openrule
-         {
-           (j\mapsto\tau),\True,\Id(V)}
-         {s \OTarrow {\tau} s}
-         \in \mathcal{T}
-\]
-and 
-\item for all $\beta_j$, $J$,  $\alpha$,  $s$, $s'$, $\Pred$, $\Post$  such that
-\[ \openrule
-         {
-           \beta_j^{j\in J},\Pred,\Post}
-         {s \OTarrow {\alpha} s'}
-         \in \mathcal{T} \] If there exists $j$ such that $\beta_j=\tau$ then we have: \[ \alpha=\tau\land s=s'\land \Pred=\True\land\Post=\Id(V) \land J=\{j\}
-\]
-\end{enumerate}
-\end{definition}
-The first statement of the definition states that the open automaton must allow a hole to do a silent action at any time, and must not observe it, i.e.
-cannot change its internal state because a hole did a $\tau$ transition.
-The second statement ensures that there cannot be in the open automaton other transitions that would be able to observe a $\tau$ action from a hole.
-The condition $J=\{j\}$ is a bit restrictive, it could safely be replaced by $\forall j\in J.\, \beta_j=\tau$, allowing the other holes to perform $\tau$ transitions too (because these $\tau$ actions cannot be observed).
-
-By definition, one weak open transition contains  several open transitions, where  each open transition can require an observable action from a given hole, the same hole might have to emit several observable actions for a single weak open transition to occur.
-Consequently, for a weak open transition to trigger, a sequence of actions from a given hole may be required.
-
-Thus, we let $\gamma$ range over sequences of action terms and use $\dotcup$ as the concatenation operator that appends sequences of action terms: given two sequences of action terms  $\gamma\dotcup\gamma '$ concatenates the two sequences.
-The operation is lifted to indexed sets of sequences:  $\set {\gamma_1}\dotcup \set {\gamma_2}$ is an indexed set such that, at each index $i$, $\set {\gamma_1}\dotcup \set {\gamma_2}$ concatenates the sequences of actions at index $i$ of $\set{\gamma_1}$ and the one at index $i$ of $\set {\gamma_2}$\footnote{One of the two sequences is empty when $i\not \in \dom(\set{\gamma_1})$ or $i\not \in \dom(\set{\gamma_2})$ .}.
-$[a]$ denotes a sequence with a single element.
-
-As required actions are now sequences of observable actions, we need an operator to build them from set of actions that occur in open transitions, i.e.
-an operator that takes a set of actions performed by one hole and produces a sequence of observable actions.
-
-Thus we define $\vis{\set\beta}$ as the mapping $\set\beta$  with only observable actions of the holes in $I$, but where each element is either empty or a list of length 1:
- \[\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}\text{ where }I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}\]
-
-As an example the $\vis{\set\beta}$ built from the transition $OT_1$ in page \pageref{OT:SimpleProt} is $\texttt{P}\mapsto [\texttt{p-send(m)}]$.
-Remark that in our simple example no $\tau$ transition involves any visible action from a hole, so we have no $\beta$ sequences of length longer than 1 in the weak automaton.
-%\TODO{en fait c'est faux ! les boucles SS\_1, SS\_2, WS\_1, WS\_2 sont aussi valides avec p\_a ou q\_b = tau, donc on peut avoir des sequences de longueur arbitraire d'actions de P et de Q}
-
-\subsection{Weak open transition definition}
-
-Because of the non-observability property (Definition~\ref{def:Non-ObsTau}), it is possible to add any number of $\tau$ transitions of the holes before or after any open transition freely.
-This property justifies the fact that we can abstract away $\tau$ transitions from holes in the definition of a weak open transition.
-
-%
-%Classically, we start by defining a derived transition relation based
-%on sequences of invisible actions.
-
-\def\InvAct{\mathcal{Inv}}
-%
-%\RAB{We let $\gamma$ range over words (of action terms) and use $\dotcup$ as the union that appends words.}
-
-\begin{definition}[Weak open transition (WOT)]\label{def:weakOT}
-A weak open transition over a
-	set $J$ of holes with sorts $\Sort_j^{j\in J}$ and a set of states $\mathcal{S}$ is 
-	a structure of the form:	
-\begin{mathpar}
- \openrule
-         {
-           \gamma_j^{j\in J'},\Pred,\Post}
-         {s \OTWeakarrow {\alpha} s'}
- \end{mathpar}
-	Where $J'\subseteq J$, $s, s'\in\mathcal{S}$ and $\gamma_j$
-        is a list of transitions of the hole $j$, with each element of the list in $\Sort_j$. $\alpha$ is an action 
-        label denoting the resulting action
-        of this open transition. \Pred\ and \Post\ are defined similarly to Definition~\ref{def:OT}. We use $\WT$ to range over sets of weak open transitions.
-
-A weak open automaton $<J,\mathcal{S},s_0,V,\WT>$ is similar to an open automaton  except that $\WT$ is a set of weak open transitions over $J$ and $\mathcal{S}$.
-\end{definition}
-
-A weak open transition labelled $\alpha$ can be seen as a sequence of open transitions that are all labelled $\tau$ except one that is labelled $\alpha$; however conditions on predicates, effects, and states must be verified for this sequence to be enactable.
-
-We are now able to build a weak open automaton from an open automaton.
-This is done in a way that resembles the process of $\tau$ saturation: we add  $\tau$ open transitions before or after another (observable or not) open transition.
-\begin{definition}[Building a weak open automaton]\label{def:buildweakOT}
-  Let $A = <J,\mathcal{S},s_0,V,\mathcal{T}>$ be an open automaton. 
-The weak open automaton \emph{derived} from $A$ is an open automaton  $<J,\mathcal{S},s_0,V,\WT>$ where $\WT$ is derived from $\mathcal{T}$ as follows: 
-%\noindent{\bf Invisible $\tau$ transitions:}
-\begin{mathpar}
- \openrule
-         {
-           \emptyset,\symb{True},\Id(s)}
-         {s \OTWeakarrow {\tau} s} \in \WT  \qquad \WTUn
- \end{mathpar}
-and
-\begin{mathpar}
-  \mprset {vskip=.5ex}
-\inferrule{
- \openrule
-         {
-           \set{\beta},\Pred,\Post}
-         {s \OTarrow {\alpha} s'} \in \mathcal{T}
-} 
-{ \openrule
-         {
-           \vis{\set{\beta}}\!,\Pred,\Post
-				 } {s \OTWeakarrow {\alpha} s'} \in \WT
-}\qquad \WTDeux
-%\inferrule{
-% \openrule
-%         {
-%           \set{\beta},\Pred,\Post}
-%         {s \OTarrow {\tau} s'} \in \mathcal{T}
-%\\
-% \openrule
-%         {
-%           \set{\gamma},\Pred\,',({x_k\gets e_k})^{k\in K}   }
-%         {s' \OTWeakarrow {\tau} s''} \in \WT
-%}
-%{ \openrule
-%         {
-%           \vis{\set{\beta}}\dotcup\set{\gamma},\Pred\land\Pred\,'\subst{\Post\,},
-%				({x_k\gets (e_k\subst{\Post\,})})^{k\in K} } 
-%         {s \OTWeakarrow {\tau} s''} \in \WT
-%}
- \end{mathpar}
- and
-%\noindent{\bf Other transitions:}
-\begin{mathpar}
-  \mprset {vskip=.5ex}
-\inferrule {\openrule
-         {
-           \set{\gamma_1},\Pred_1,\Post_1   }
-         {s \OTWeakarrow {\tau} s_1} \in \WT
-\qquad
-\openrule
-         {
-           \set{\gamma_2},\Pred_2,\Post_2  }
-         {s_1 \OTWeakarrow {\alpha} s_2} \in \WT
-\qquad
-\openrule
-         {
-           \set{\gamma_3},\Pred_3,\Post_3  }
-         {s_2 \OTWeakarrow {\tau} s'} \in\WT
-\\
-\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land \Pred_3\subst{\Post_2\shortotimes\Post_1}
-\\
-\set{\gamma}=\set{\gamma_1}\dotcup \set{\gamma_2}\subst{\Post_1}\dotcup\set{\gamma_3}\subst{\Post_2\shortotimes \Post_1}\\
-\alpha'=\alpha\subst{\Post_1}
-}
-{
-\openrule
-         {\set{\gamma}
-           ,
-		\Pred,
-				\Post_3\shortotimes\Post_2\shortotimes\Post_1} 
-         {s \OTWeakarrow {\alpha'} s'} \in\WT
-} \WTTrois
-\end{mathpar}
-
-\end{definition}
-Rule $\WTUn$ states that it is always possible to do a null $\tau$ transition, where the state is unchanged and the holes perform no action.
-Rule~$\WTDeux$ states that each open transition can be considered as a weak open transition.
-The last rule is the most interesting:  Rule~$\WTTrois$ allows any number of $\tau$ transitions before or after any weak open transition.
-This rules carefully composes predicates, effects, and actions of the holes, indeed in the rule, predicate $\Pred_2$ manipulates variables of $s_1$ that result from the first weak open transition.
-Their values thus depend on the initial state but also on the effect (as a substitution $\Post_1$) of the first weak open transition.
-In the same manner, $\Pred_3$ must be applied the joint substitution $\Post_2\shortotimes\Post_1$.
-Similarly, effects on variables must be applied to obtain the global effect of the composed weak open transition, it must also be applied to observable actions of the holes, and to the global action of the weak open transition.
-
-%% \begin{figure}[ht]
-%%    \centerline{\includegraphics[width=12cm]{ATG/WOT1}}
-%%   \caption{Construction of the Weak Open transition WOT1}
-%%    \label{WOT1}
-%% \end{figure}
-
-%% \begin{figure}[ht]
-%%    \centerline{\includegraphics[width=11cm]{ATG/WOT2}}
-%%   \caption{Construction of WOT2}
-%%    \label{WOT2}
-%% \end{figure}
-
-\begin{figure}[ht]
-   \centerline{\includegraphics[width=13cm]{XFIG/WOT2-result}}
-  \caption{Construction of an example of weak open transition}
-   \label{WOT2}
-\end{figure}
-
-\begin{example} Figure \ref{WOT2} shows the construction of one of the weak transitions of the Specification OA.
-On the top we show the subset of the original open automaton (from Figure \ref{SimpleProtCounter:SpecOA}) considered here, and at the bottom the generated weak transition.
-For readability, we abbreviate the weak open transitions encoded by $\openrule   {\{\}, True,	() } {s \OTWeakarrow \tau s'}$  as $W_\tau$.
-The weak open transition shown here is the transition delivering the result of the algorithm to hole $Q$ by applying rules: \WTUn,\WTDeux, and \WTTrois.
-First rule \WTUn~ adds a $WT_\tau$ loop on each state.
-Rule \WTDeux~ transforms each 3 OTs into WOTs.
-Then consider application of Rule \WTTrois~ on a sequence 3  WOTs.
-$\openrule
-         {\{\}, True,
-			(\texttt{b\_ec}\gets \texttt{b\_ec}+1) }
-         {\text{b1}\OTWeakarrow \tau \text{b1}}$; $\openrule
-         {\{\}, True,
-			(\texttt{b\_ec}\gets \texttt{b\_ec}+1) }
-         {\text{b1} \OTWeakarrow \tau \text{b1}}$;  $\openrule
-         {\{\}, True,
-			() }
-         {\text{b1} \OTWeakarrow \tau \text{b1}}$. Then Rule \WTTrois~ produces  $\openrule
-         {\{\}, True,
-			(\texttt{b\_ec}\gets \texttt{b\_ec}+2) }
-         {\text{b1} \OTWeakarrow \tau \text{b1}}$. We can  can iterate this construction an arbitrary number of times, getting for any natural number $n$ the weak open transition:
-  $\openrule
-         {\emptyset, True,
-			(\texttt{ec}\gets \texttt{ec}+n) }
-        {\text{b1} \OTWeakarrow \tau \text{b1}}\, \forall n \geq 0$.
-Finally,  applying again \WTTrois, and using the central open transition having \texttt{\nounderline{out(b\_msg,b\_ec)}}  as $\alpha$, we get the resulting weak open transition between b1 and b0 (as shown in Figure \ref{WOT2}).
-Applying the substitutions finally yields the weak transition $WS_7$ in Figure  \ref{SimpleProtCounter:WeakSpecOA}.
-
- %     $\openrule
- %        {\{\texttt{Q}\mapsto\texttt{q-revc(ec)}\subst{ec\gets ec+n}\}, True,
-%			(\texttt{ec}\gets \texttt{ec}+n) }
- %        {b1 \OTWeakarrow {\nounderline{\texttt{out(m,ec)}}\subst{ec\gets ec+n}} b0} \forall n \geq 0$. 
-\end{example}
-
-  \begin{example}
-    Figures \ref{SimpleProtCounter:WeakSpecOA} and \ref{SimpleProtCounter:ImplWOA2} respectively show the weak automata of the simple protocol specification and implementation.
-We encode weak open transitions  by $WS$ on the specification model and by $WI$ on the implementation model.
-
-\begin{figure}[h]
-   \centerline{\includegraphics[width=15cm]{XFIG/SPSpecWeakOpen}}
-  \caption{Weak Open Automaton of the Specification}
-   \label{SimpleProtCounter:WeakSpecOA}
-\end{figure}
-
- For readability, we do not include the full details of the Implementation weak open transitions in Figure \ref{SimpleProtCounter:ImplWOA2}, but we show some examples below and the full list is included in Appendix \ref{Appendix:FullExample}.
-First, let us point out that the weak OT loops ($WI_1$,$WI_2$ and $W_\tau$) on state ${000}$ are also present in all other states, we did not repeat them.
-Then many WOTs are similar, and numbered accordingly as 3, 3a, 3b, 3c and 8, 8a, 8b, 8c respectively: they only differ by the name of the state variables in their respective source or target states; the "variant" WOTs appear in blue in   Figure \ref{SimpleProtCounter:ImplWOA2}.
-\end{example}
-
-%\begin{figure}[h]
-  % \centerline{\includegraphics[width=11cm]{XFIG/SimpleProtImpl-WOA}}
- % \caption{Weak Open Automaton of the implementation}
- %  \label{SimpleProtCounter:ImplWOA}
-%\end{figure}
-
-\begin{figure}[h]
-   \centerline{\includegraphics[width=11cm]{XFIG/SimpleProtImpl-WOA2}}
-  \caption{Weak Open Automaton of the implementation}
-   \label{SimpleProtCounter:ImplWOA2}
-\end{figure}
-
-Now let us give some details about the construction of the weak automaton of the implementation pNet, obtained by application of the weak rules as explained above.
-We concentrate on weak open transitions $WI_3$ and $WI_4$.
-Let us denote as $post_n$ the effect (substitution) of the strong open transitions $SI_n$ from Figure \ref{SimpleProtCounter:ImplOA}:
-\smallskip
-
-$post_3 = (\texttt{s\_msg}\gets \texttt{m}, \texttt{s\_ec}\gets 0)$
-
-$post_4 = (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec})$
-
-$post_5 = ()$
-
-$post_6 = (\texttt{s\_ec}\gets \texttt{s\_ec+1})$
-
-\medskip
-
-Then the effect of one single $100 \xrightarrow{OT_4} 210 \xrightarrow{OT_5} 220 \xrightarrow{OT_6} 100$ loop is:
-\smallskip
-
-$post_{456} = post_6 \shortotimes\ post_5 \shortotimes\ post_4
-= (\texttt{s\_ec}\gets \texttt{s\_ec}+1)$.
-\footnote{when showing  the result of $Posts$ composition, we will Z omit the identity substitutions introduced by the $\shortotimes$ definition in page \pageref{def:substitutions}}
-\medskip
-
-So if we denote ${post_{456*}}$ any iteration of this loop, we get ${post_{456*}} = (\texttt{s\_ec}\gets \texttt{s\_ec}+n)$ for any $n\ge 0$, and the \Post~ of the weak OT  $WI_{3}$ is:\\
- $Post_3 = post_{456*}\shortotimes\ post_3 = (\texttt{s\_msg}\gets m, \texttt{s\_ec}\gets n), \forall n\ge 0$ and \Post~ of  $WI_{3a}$  is:\\ $post_4\shortotimes {post_{456*}}\shortotimes\ post_3 = (\texttt{m\_msg}\gets m, \texttt{m\_ec}\gets n), \forall n\ge 0$.
-\medskip
-
-We can now show some of the weak OTs of Figure \ref{SimpleProtCounter:ImplWOA2} (the full table is included in Appendix \ref{Appendix:FullExample}) :
-
-\TODO{Qu'est-ce qu'on avait dit ici pour "$n$" ? a droite ou a gauche, mais pas les deux ?Et est-ce qu'on le laisse en italique dans les expressions, pour souligner son statut de parametre ?.
-Dans tous les cas expliquer ?}
-\smallskip
-
-$ WI_1 = \openrule
-{\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], ()}
-{s \OTWeakarrow {\texttt{p-a}} s}
-$ (for any  $s \in S$)
-
-$ WI_3(n) = \openrule
-  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
-    (\texttt{s\_msg}\gets \texttt{m}, \texttt{s\_ec}\gets n)}
-  {000 \OTWeakarrow {\nounderline{\texttt{in(m)}}} 100}
-        $$\forall n\ge 0$
-
-$ WI_4(n) = \openrule
-         {\{\}, True, 
-   (\texttt{m\_msg}\!\gets\! \texttt{s\_msg}, \texttt{m\_ec}\!\gets\! \texttt{s\_ec}+n, \texttt{s\_ec}\!\gets\! \texttt{s\_ec}+n)}
-         {100 \OTWeakarrow {\tau} 210}
-        $$\forall n\ge 0$
-
-$ WI_{456}(n) = \openrule
-         {\{\}, True, 
-    (\texttt{s\_ec}\gets \texttt{s\_ec}+n)}
-  {100 \OTWeakarrow {\tau} 100}
-        $$\forall n\ge 0$
-
-   \medskip     
-The  \Post~of of the weak OT $ WI_{6a}$ is:\\
-
-$
-\begin{array}{ll}
-Post_{6a}= post_{4}\shortotimes\ post_{456*}\shortotimes\ post_{6} =&  (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec})\,
-\shortotimes \\ &(\texttt{s\_ec}\gets \texttt{s\_ec}+n) 
-\shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+1) =\\
-&(\texttt{m\_msg}\!\gets \texttt{s\_msg}, \texttt{m\_ec}\!\gets \texttt{s\_ec}+1\!+\!n, \texttt{s\_ec}\!\gets \texttt{s\_ec}+1\!+\!n)
-\end{array}$\\
-
-$ WI_{6a}(n) = \openrule
-         {\{\}, True, 
-         (\texttt{m\_ec}\gets \texttt{s\_ec}+1+n, \texttt{s\_ec}\gets \texttt{s\_ec}+n)}
-         {220 \OTWeakarrow {\tau} 210} \forall n\ge 0
-         $
-
-\medskip
-$Post_{8c}= post_{8}\shortotimes\ post_{7}\shortotimes\ post_{4}\shortotimes\ post_{456*} 
-= (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_msg}+1+n), \forall n\ge 0$
-\medskip  
-$WI_{8c}(n) = \openrule
-         {\{\texttt{Q}\mapsto \texttt{q-recv(s\_msg,s\_ec}+n)\}, True, (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_msg}+1+n)}
-         {210 \OTWeakarrow {\nounderline{\texttt{out(s\_msg,s\_ec}+n)}} 202}\forall n\ge 0$
-
-\subsection{Composition properties: composition of weak open transitions}
-We now have two different semantics for open pNets: a strong semantics, defined  as an open automaton, and as a weak semantics, defined as a weak open automaton.
-Like the open automaton, the weak open automaton features valuable composition properties.
-We can exhibit  a composition property and a decomposition property that relate open pNet composition with their semantics, defined as weak open automata.
-These are however technically more complex than the ones for open automata because each hole performs a set of actions, and thus a composed transition is the composition of one transition of the top-level pNet and a sequence of transitions of the sub-pNet that fills its hole.
-They can be found as Lemmas~\ref{lem-decomposeWOT}, Lemma~\ref{lem-Weakcompose1}, and Lemma~\ref{lem-Weakcompose} in Appendix~\ref{sec:app-composition}.
-
-\subsection{Weak FH-bisimulation}
-For defining a bisimulation relation between weak open automata, two options are possible.
-Either we define a simulation similar to the strong simulation but based on open automata, this would look like the FH-simulation but would need to be adapted to weak open transitions.
-Or we define directly and classically a weak FH-simulation as a relation between two open automata, relating the open transition of one open automaton with the transition of the weak open automaton derived from the second one.
-
-The definition below specifies how a set of weak open transitions can simulate an open transition, and under which condition; this is used to relate, by weak FH-bisimulation, two open automata by reasoning on the weak open automata that can be derived from the strong ones.
-This is defined formally as follows.
-
-\begin{definition}[Weak FH-bisimulation]\label{def-Weak-bisim} ~\\
-\noindent
-Let $A_1 = <J,\mathcal{S}_1, s_0,V_1,
-    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0, V_2, \mathcal{T}_2>$ be open automata with disjoint state variables.
-Let $<J,\mathcal{S}_1, s_0,V_1,
-    \WT_1>$ and $<J,\mathcal{S}_2,t_0, V_2, \WT_2>$ be the
-weak open automata derived from $A_1$ and $A_2$ respectively.
-Let $\mathcal{R}$ a relation over
-$\mathcal{S}_1$ and $\mathcal{S}_2$, as in Definition~\ref{def-FH-bisim}.
-
-Then 
-   $\mathcal{R}$ is a weak FH-bisimulation iff for any  states
-$s\in\mathcal{S}_1$ and
-$t\in\mathcal{S}_2$ such that $(s,t|\Pred)\in\mathcal{R}$, we 
-   have the following:
-
- \begin{itemize}
- \item  For any open transition $OT$ in $\mathcal{T}_1$:
- \begin{mathpar}
-     \openrule
-         {
-           \beta_j^{j\in J'},\Pred_{OT},\Post_{OT}}
-         {s \OTarrow {\alpha} s'}
-
-\end{mathpar}
- there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {t \OTWeakarrow {\alpha_x} t_x}
-\end{mathpar}
- such that  $\forall x, \{j\in J'|\beta_j\neq\tau\}=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
- and  \\
- $\Pred \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
-   \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
-     \!\land\! \alpha\!=\!\alpha_x\! \land\!  
-     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}$
-
- \item  and symmetrically any open transition from $t$ in $\mathcal{T}_2$ can be 
-      covered by a set of weak transitions from $s$ in $\WT_1$.
- \end{itemize}
-
-Two pNets are weak FH-bisimilar if there exists a relation between their associated 
-automata that is a Weak FH-bisimulation and their initial states are in the relation, i.e. 
-the predicate associated to the relation between the initial states is \True.
- \end{definition}
-
-Compared to strong bisimulation, except the obvious use of weak open transitions to simulate an open transition, the condition on predicate is slightly changed concerning actions of the holes.
-Indeed only the visible actions of the holes must be compared and they form a list of actions, but of length at most one.
-
-\LUDO{il faudrait mieux introduire le paragraphe ci dessous pour expliquer ce qu'il fait ici}
-In practice, we are dealing with finite representations of the (infinite) open automata.
-In \cite{hou:hal-02406098}, we defined a slightly modified definition of the ``coverage'' proof obligation, in the case of strong FH-Bisimulation.
-This modification is required to manage in a finite way all possible instantiations of an OT.
-In the case of weak FH-Bisimulation, the proof obligation from definition \ref{def-Weak-bisim} becomes:
-
- $\forall fv_{OT}. \{ \Pred \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
-  \left[\exists fv_{OT_x}.\\
-    \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
-     \!\land\! \alpha\!=\!\alpha_x\! \land\!  
-     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)\right]\}}$
-
-In which $fv_{OT}$ denotes the set of free variables of all expressions in $OT$.
-
-\medskip
-Our first important result is that Weak FH-bisimilarity is an equivalence in the same way as strong FH-bisimilarity:
-
-\begin{theorem}[Weak FH-Bisimulation is an equivalence]\label{thm-weak-equiv} Suppose $\mathcal{R}$ 
-is a weak FH-bisimulation. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
-reflexive, symmetric and transitive.
-\end{theorem}
-The proof  is detailed in Appendix \ref{app-WFH-equiv}, it follows a similar pattern as the proof that strong FH-bisimulation is an equivalence, but technical details are different, and in practice we rely on a variant of the definition of weak FH-bisimilarity; this equivalent version simulates a \emph{weak} open transition with a set of weak open transition.
-The careful use of the best definition of weak FH-bisimilarity makes the proof similar to the strong FH-bisimulation case.
-
-\paragraph{Proving bisimulation in practice}
-
-\subsection{Weak bisimulation for open pNets}
-
-Before defining a weak open automaton for the semantics of open pNets,
-it is necessary to state under which condition a pNet is unable to
-observe silent actions of its holes. In the setting of pNets this can
-simply be expressed as a condition on the synchronisation
-vectors. Precisely, the set of synchronisation vectors must contain
-vectors that let silent actions go through the pNet,
-i.e. synchronisation vectors where one hole does a $\tau$ transition,
-and the global visible action is a $\tau$. Additionally, no other
-synchronisation vector must be able to react on a silent action from a
-hole, i.e. if a synchronisation vector observes a $\tau$ from a hole
-it cannot synchronise it with another action nor emit an action that
-is not $\tau$. This is formalised as follows:
-
-\begin{definition}[Non-observability of silent actions for pNets]\label{def:non-obspNet}~\\
-A pNet $\mylangle \pNet_i^{i\in I} , \Sort_j^{j\in J}, \set{\symb{SV}}\myrangle$
- \emph{cannot observe silent actions} if it verifies:\\ $\forall i\in I\uplus J.\, \SV{(i\mapsto \tau)}{\tau}{\True}\in \set{\symb{SV}}$ and 
-\begin{equation*}
-%\begin{split}
-\forall \left(\SV{{(\alpha_i)}^{i\in I'}} 
-{\alpha'} 
-{e_b}\in \set{\symb{SV}}\right), %&
-\forall i\in I'\cap J,\, \alpha_i=\tau \implies %\\
-%& 
-\alpha'=\tau ~\land~ %\\
-%&
-I'=\{i\}
-%\end{split}
-\end{equation*}
-\end{definition}
-
-With this definition, it is easy to check that the open automaton that gives the semantics of such an open pNet cannot observe silent actions in the sense of Definition~\ref{def:Non-ObsTau}:
-
-\begin{property}[Non-observability of silent actions]
-The open semantics of a pNets that cannot observe silent actions is an open automaton that  cannot observe silent actions.
-\end{property}
-
-%\TODO{question : we could merge prop 1 and def above, is it better?}
-
-Under this condition, it is safe to define the weak open automaton that provides a weak semantics to a given pNet.
-This is simply obtained by applying Definition~\ref{def:buildweakOT} to generate a weak open automaton from the open automaton that is the strong semantics of the open pNet, as provided by Definition~\ref{def:operationalSemantics}.
-
-\begin{definition}[Notation: Semantics of pNets as a weak open automaton]
-Let $A$ be the open automaton expressing the semantics of an open pNet $\pNet$; let $<J,\mathcal{S},s_0, V, \WT>$ be the weak open automaton derived from $A$; this weak open automaton defines the weak semantics of the pNet $\pNet$.
-Then, we denote $\pNet \models \WOT$ whenever $\WOT\in\WT$.
-\end{definition}
-
-\subsection{Properties of weak bisimulation for open pNets}
-
-When silent actions cannot be observed, weak bisimulation is a congruence for open pNets: if $P$ and $Q$ are weakly bisimilar to $P'$ and $Q'$ then the composition of $P$ and $Q$ is weakly bisimilar to the composition of $P'$ and $Q'$, where composition is the hole replacement operator: 	$\pNet[\pNetQ]_{j}$ and
-	$\pNet'[\pNetQ']_{j}$ are weak FH-bisimilar. This can be shown by proving the two following theorems.
-The detailed proof of these theorem can be found in Appendix~\ref{sec:app-composition}.
-The proof strongly relies on the fact that weak FH-bisimulation is an equivalence, but also on the composition properties for open automata.
-
-\begin{theorem}[Congruence for  weak bisimulation]\label{weak-thm-congr-eq}
-	Consider an open pNet:
-	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
-	\set{\symb{SV}}\myrangle$ that cannot observe silent actions.
-	Let $j_0\in J$ be a hole. Let $\pNetQ$ and $Q'$ be two weak FH-bisimilar pNets such that 
-	$\Sortop(\pNetQ)=\Sortop(\pNetQ')=\Sort_{j_0}$\footnote{Note that $\Sortop(\pNetQ)=\Sortop(\pNetQ')$ is 
-	ensured by 
-	weak bisimilarity.}. Then 
-	$\pNet[\pNetQ]_{j_0}$ and 
-	$\pNet[\pNetQ']_{j_0}$ are weak FH-bisimilar.
-\end{theorem}
-
-\begin{theorem}[Context equivalence for  weak bisimulation]\label{weak-thm-ctxt-eq}
-	Consider two  open pNets
-	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
-	\set{\symb{SV}}\myrangle$ and 	$\pNet' = \mylangle {\pNet'}_i^{i\in I}, 
-	\Sort_j^{j\in 
-	J}, 	\set{\symb{SV'}}\myrangle$ that are weak FH-bisimilar
-	(recall they must have the same holes to be bisimilar) and that cannot observe silent actions.
-	Let $j_0\in J$ be a hole, and $\pNetQ$ be a pNet such that $\Sortop(\pNetQ)=\Sort_{j_0}$. Then 
-	$\pNet[\pNetQ]_{j_0}$ and 
-	$\pNet'[\pNetQ]_{j_0}$ are weak FH-bisimilar.
-\end{theorem}
-
-Finally, the previous theorems can be composed to state a general theorem about 
-composability and weak FH-bisimilarity.
-
-\begin{theorem}[Composability of weak bisimulation]\label{weak-compos}
-	Consider two weak FH-bisimilar pNets with an arbitrary number of holes, such that the two pNets cannot observe silent actions. When replacing, 
-	inside those two original pNets, a subset of the holes by weak FH-bisimilar pNets, we 
-	obtain two weak FH-bisimilar pNets.
-\end{theorem}
-
-\subsection{Running example}
-In section \ref{sec:weak} we have shown the full satured weak automaton for both the specification and the implementation of the simple protocol.
-We will show here how we can check if some given relation between these two automata is a weak FH-Bisimulation.
-
-\medskip
-\noindent
-Preliminary remarks:
-  \begin{itemize}
-    \item Both pNets trivialy verify the ``non-observability''
-      condition: the only vectors having $\tau$ as an action of a
-      sub-net are of the form ``$< -, \tau, -> -> \tau$''.
-    \item We must take care of variable name conflicts: in our example, the state variables of the 2 systems already have different names, but the action parameters occurring in the transitions (m, msg, ec) are the same, that is not correct.
-In the tools, this is managed by the static semantic layer; in the following example, we have renamed all conflicting variables with 1 for the Spec, and 2 for the Impl.
-    \end{itemize}
-
-  \medskip
-  Now consider the relation $\mathcal{R}$ defined by the following triples:
-
-  \begin{tabular}{|c|c|l|}
-\hline
-    Spec state & Impl state & Predicate\\
-    \hline
-    b0 & $000$ & True\\
-    b0 & $202$ & True\\
-    b1 & $100$ & $\texttt{b\_msg = s\_msg} \land \texttt{b\_ec = s\_ec}$\\
-    b1 & $210$ & $\texttt{b\_msg = m\_msg} \land \texttt{b\_ec = m\_ec}$\\
-    b1 & $220$ & $\texttt{b\_msg = s\_msg} \land \texttt{b\_ec = s\_ec}$\\
-    b1 & $201$ & $\texttt{b\_msg = r\_msg} \land \texttt{b\_ec = r\_ec}$\\
-    \hline
-    \end{tabular}
-
-  \medskip
-  Checking that $\mathcal{R}$ is a weak FH-Bisimulation means checking, for each of these triples, that each (strong) OT of one the states corresponds to a set of WOTs of the other, using the conditions from Definition \ref{def-Weak-bisim}.
-  We give here two examples.
-
-  \medskip
-  Consider the second triple from the table, and transition $SS_3$ from state $b0$. Its easy to guess that it will correspond to $WI_3(0)$ of $202$.
-
-  $ SS_3 = \openrule
-  {\{\texttt{P}\mapsto \texttt{p-send(m1)}\}, True,
-    (\texttt{b\_msg}\gets \texttt{m1}, \texttt{b\_ec}\gets 0)}
-  {\text{b0} \OTarrow {\nounderline{\texttt{in(m1)}}} \text{b1}}
-  $
-
-$ WI_3(0) = \openrule
-  {\{\texttt{P}\mapsto \texttt{p-send(m2)}\}, True,
-    (\texttt{s\_msg}\gets \texttt{m2}, \texttt{s\_ec}\gets 0)}
-  {000 \OTWeakarrow {\nounderline{\texttt{in(m2)}}} 100}
-  $
-
-  Let check formally the conditions:
-
-\begin{itemize}
-  \item Their sets of active (non-silent) holes is the same: $J' = J_x = \{\texttt{P}\}$.
-  \item Triple ($\text{b1},  100,  \texttt{b\_msg = s\_msg} \land \texttt{b\_ec = s\_ec}$) is in $\mathcal{R}$.
-  \item The verification condition \\
-    $\forall fv_{OT}. \{ \Pred \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
-   \left[\exists fv_{OT_x}.
-  \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
-     \!\land\! \alpha\!=\!\alpha_x\! \land\!  
-     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)\right]\}}$
-
-\medskip Gives us:
-
-$\forall \texttt{m1}. \{True \land True\hspace{3mm} \implies
-\exists \texttt{m2}. \\
-(\texttt{[p-send(m1)]} = \texttt{[p-send(m2)]}
-\land True
-\land \nounderline{\texttt{in(m1)}} = \nounderline{\texttt{in(m2)}} \land 
-\\
-(\texttt{b\_msg\!\!
-= \!\!s\_msg} \land \texttt{b\_ec\!\!
-=\!\!
-s\_ec}) \subst{(\texttt{b\_msg}\!\gets\!
-\texttt{m1}, \texttt{b\_ec}\!\gets\!
-0)\uplus (\texttt{s\_msg}\!\gets\!
-\texttt{m2},\texttt{s\_ec}\!\gets\!
-0)})\}$
-
-\medskip That reduces to:
-
-$\forall \texttt{m1}. \exists \texttt{m2}.
-(\texttt{p-send(m1)} = \texttt{p-send(m2)}
-\land \texttt{in(m1)} = \texttt{in(m2)}
-\land \texttt{m1}=\texttt{m2} \land 0=0)$
-
-\medskip That is a tautology.
-
-\end{itemize}
-
-  \bigskip
-  Now consider the $3^{rd}$ triple from the table, and transition $SI_{4}$ from state $100$ to state $210$. It should correspond to $WS_4(0)$ of $b1$, where:
-
-  $ SI_{4} = \openrule
-         {\{\}, True, (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec}, \texttt{s\_ec}\gets \texttt{s\_ec})}
-         {100 \OTarrow {\tau} 210}
-         $
-
-  $ WS_4(n) = \openrule
-         {\{\}, True, (\texttt{b\_ec}\gets \texttt{b\_ec}+n)}
-         {\text{b1} \OTWeakarrow {\tau} \text{b1}}
-         \ \forall n\ge 0
-         $
-
-  \medskip       A similar reasonning gives us
-\begin{itemize}
-  \item No active holes and the pair of ressulting states $<210,b1>$ is in $\mathcal{R}$.
-\item $fv(SI_4) = \{\}, fv(WS_4(n)) = \{n\}$,
-\item and the verification condition\\
-
-         $(\texttt{b\_msg} = \texttt{s\_msg} \land \texttt{b\_ec} = \texttt{s\_ec}) \land True\hspace{3mm} \implies
-\exists n.(True \land \tau=\tau \land \\ (\texttt{b\_msg} = \texttt{m\_msg} \land \texttt{b\_ec} = \texttt{m\_ec})  \subst{\texttt{m\_msg}\!\gets\!
-\texttt{s\_msg}, \texttt{m\_ec}\!\gets\!
-\texttt{s\_ec}, \texttt{s\_ec}\gets \texttt{s\_ec}}
-\uplus \subst{\texttt{b\_ec}\gets \texttt{b\_ec}+n})
-$
-
-is easily proved True for $n=0$.
- \end{itemize}
-
-\section{Related Works}\label{sec:RW}
-
-\TODO{retravailler le paragraphe ci dessous}
-In
-\cite{Johnson:2013:CBSE,Johnson:2014:qosa}, the authors investigate several methodologies for the compositional verification of software systems, with the aim to verify reconfigurable component systems.
-To improve scaling and compositionality, the authors  decouple the verification problem that is to be resolved by a SMT (satisfiability modulo theory) solver into independent sub-problems on independent sets of variables.
-These works clearly highlight the interest of incremental and compositional verification in a very general setting.
-By adding more structure to the composition model and designing a dedicated bisimulation theory, we show here how to enforce a compositional proof system that is more powerful than independent sets of variables.
-Our theory has also been encoded into an SMT solver and it would be interesting to investigate how the examples of evolving systems studied by the authors could be encoded into pNet and verified by our framework.
-However, the models of Johnson et al.
-are quite different from ours, in particular they are much less structured, and translating them is clearly outside the scope of this article.
-Additionally, the more compositional constraint resolution provided by the authors could also be interesting to make our SMT proofs scale better (inside a single pNet for example), the integration of the Z3 framework described in \cite{Johnson:2014:qosa} with our proof theory for open pNets would also be worth investigating from a practical point of view.
-One major different however is that pNets in their current state are not much adapted to probabilistic verification contrarily to \cite{Johnson:2014:qosa} but they are better suited to verify complex behavioural properties.
-
-\ERIC{J'ai copie/colle ici le Related Work que Zechen a mis dans notre
-  papier bisim...
-  Pas tres satisfaisant pour les aspects Weak, mais quelques inputs a
-  regarder}
-
-To the best of our knowledge, there is no other research works on the Bisimulation Equivalence between such complicate(open, symbolic, parameterised, with loops and assignments) system models, with providing fully complete algorithms.
-For the sake of completeness, we give a brief overview of other Symbolic Bisimulation researches.
-
-One line of research is providing Symbolic Bisimulation for different model or language. 
-In Calder's work\cite{calder2001symbolic}, they define a symbolic semantic for full LOTOS, with a symbolic bisimulation over it;
-Borgstrom et al., Delaune et al.
-and Buscemi et al.
-provide symbolic semantic and equivalence for different variants of pi calculus respectively\cite{borgstrom2004symbolic}\cite{delaune2007symbolic}\cite{buscemi2008open}, and later in 2012 Liu's work provided symbolic bisimulation  for full applied pi calculus\cite{liu2010complete};
-The most recent work, Feng et al. provide a symbolic bisimulation for quantum processes
-\cite{feng2014symbolic}.
-All the above works, didn't give a complete approach for verification, and the models on which these works based are simpler or different than ours.
-
-Another line of research is devising the algorithm for computing symbolic Bisimulation Equivalence.
-In Dovier's work, they provide a rank-based algorithm, layering the input model to compute bisimulation\cite{dovier2002rank}. 
-Baldan et al. also focus on open systems, using a logical programming language \emph{Prolog} to model the systems and compute Bisimulation\cite{baldan2001compositional}.
-Wimmer et al. present a signature-based approach to compute Bisimulation, implemented by using BDDs\cite{wimmer2006sigref}.
-Lin present a symbolic bisimulation between symbolic transition graph with assignments(STGA), as mentioned in \emph{Introduction}, bring us lots of inspirations.
-
-\section{Conclusion and Discussion}
-\label{section:conclusion}
- pNets (Parameterised Networks of Automata) is a formalism adapted to the representation of the behaviour of a parallel or distributed systems.
-One  strength of pNets is their parameterised nature, making them adapted to the representation of systems of arbitrary size, and making the modelling of parameterised system possible.
-Parameters are also crucial to reason on interaction protocols that can address one entity inside an indexed set of processes.
-pNets have been successfully used to represent behavioural specification of parallel and distributed components and verify their correctness~\cite{AmeurBoulifa2017,HKM-FASE16}.
-VCE is the specification and verification platform that uses pNets as an intermediate representation.
-
-Open pNets are pNets with holes; they are adapted to represent processes parameterised by the behaivour of other processes, like composition operators or interaction 
-protocols that synchronize the actions of processes that can be plugged afterwards. Open
-pNets are hierarchical composition of automata with holes and parameters. We
-defined here a semantics for open pNets and a complete bisimulation theory for them. 
-The semantics of open pNets relies on the definition of open automata that are automata with holes and parameters, but no hierarchy.
-Open automata are somehow labelled transition systems with parameters and holes, a notion that is useful to define semantics, but makes less sense when modelling a system, compared to pNets.
-To be precise, it is on open automata that we define our bisimulation relations.
-
-This article defines a strong and a weak bisimulation principles that are adapted to parameterised systems and hierarchical composition.
-Our bisimulation principle handles pNets parameters in the sense that two states might be or not in relation depending on the value of parameters.
-Our strong  bisimulation is compositional by nature in the sense that bisimulation is maintained when composing processes.
-We also identified a simple and realistic condition on the semantics of non-observable actions that allows weak bisimulation to be also compositional.
-Overall we believe that this article paved the way for a solid theoretical foundation for compositional verification of parallel and distributed systems.
-
-We are currently extending this work,  looking at  both further properties of 
-FH-bisimulation, but also
-the relations with existing equivalences on closed systems.
-We also plan to apply open pNets to the study of complex composition
-operators in a symbolic way, for example in the area of parallel
-skeletons, or distributed algorithms.
-We have developped tool support for computing the
-symbolic semantics in term of open-automata \cite{QBMZ-AVOCS18}, and have
-developed algorithms to check strong FH-bisimulation \cite{hou:hal-02406098}.  
-Naturally we are now working toward an implementation of weak FH-Bisimulation. 
-The challenges here, in the context of uour symbolic systems, is not so much algorithmic complexity,
-as was the case with classical weak bisimulation on finite models, but decidability and termination.
-Two main directions should be explored, either with an explicite construction of the weak transition, but this step in
-itself may introduce non-termination, or a direct implementation of the weak bisimulation definition, without
-constructing the weak automaton. We can expect that optimisations here in the symbolic setting would be quite different from the classical case.
-
-\bibliographystyle{lncs/splncs}
-
-% \bibliography{oasis,biblio}
-\bibliography{biblio}
-
-\newpage
-\appendix    
-\section{Proof on FH-bisimulation}
-\subsection{Bisimulation is an equivalence: Proof of Theorem~\ref{thm-equiv}}\label{thm-equiv-proof}~\\
-        \emph{Suppose $\mathcal{R}$ 
-       	is an FH-bisimulation. Then $\mathcal{R}$ is an equivalence, that is, 
-       	$\mathcal{R}$ is 
-       	reflexive, symmetric and transitive.
-       	}
-%%% A PROOF WITH CONSTRUCTIVE AERGUMENTS BUT THAT DOES NOT WORK
-
-%       \begin{proof}
-%
-%       It is trivial to check reflexivity and symmetry. Here we focus on the
-%transitivity. 
-%To prove transitivity of strong FH-bisimulation on pNets it is sufficient to prove 
-%transitivity of the strong FH-bisimulation on states of their Open Automata. Consider 3 
-%open automata 
-%$\mathcal{T}_1$, $\mathcal{T}_2$, $\mathcal{T}_3$ and states $s^1$, $s^2$, $s^3$ in 
-%those 
-%automata\footnote{We omit the constraints stating that each $s^i_x$ is in the states of 
-%$\mathcal{T}_i$ for the sake of readability}.
-%Suppose we have $\mathcal{R}$ an FH-bisimulation relation between states of 
-%$\mathcal{T}_1$ and of  $\mathcal{T}_2$; members of $\mathcal{R}$ are of the form 
-%$(s^1,s^2|\Pred)$.
-%Suppose we also  have $\mathcal{R}'$ an FH-bisimulation relation between states of 
-%$\mathcal{T}_2$ and of  $\mathcal{T}_3$; members of $\mathcal{R}2$ are of the form 
-%$(s^2,s^3|\Pred\,')$.
-%We use $\fv$ a function returning the free variables of a term/automaton.
-%
-%Let $\mathcal{R}''$ be the relation (We denote $\Phi$ a set of renamings): 
-%
-%%\begin{mathpar}
-%%\inferrule{}
-%%{}
-%%\end{mathpar}
-%
-%\[\mathcal{R}'' = \Big\{(s^1,s^3|\Pred\,'')\Big|
-%\displaystyle
-% \begin{array}[t]{l}\exists (s^2_p)^{p\in P}.\,\exists (\Phi_p)^{p\in P}.\,\\
-%\quad 
-%	\big(\begin{array}{l}
-%	\forall p\in P.\, (s^1,s^2_p|\Pred)\in\mathcal{R}\land 
-%	(s^2_p,s^3|\Pred\,')\in\mathcal{R}'\land \\
-%	 \forall\ \phi\in\Phi_p.\,
-%	  \fv((\Pred\land\Pred')\phi)\subseteq \fv(\mathcal{T}_1)\cup\fv(\mathcal{T}_3) \land
-%	  \dom(\phi)\subseteq \fv(\mathcal{T}_2)
-%	\end{array}
-%	\big)\\
-%\quad
-%\land ~\Pred'' =\displaystyle\bigvee_{\begin{array}{l}
-%	p\in P\\\phi\in \Phi_p
-%	\end{array}} (\Pred\land\Pred\,')\phi
-%	
-%\end{array}\Big\}
-%\]
-%%(s^1,s^2|\Pred)\in\mathcal{R}\\ (s^2,s^3|\Pred\,')\in\mathcal{R}' 	
-%%}\!\!\!\!\!\exists \phi.\begin{array}[t]{l} \\
-%%\land 
-%%\\
-%%\land 
-%%\\
-%\TODO{s2p is the family of states that relate s1 and s2 big phi is the set of renamings 
-%for each s2 in the family}
-%
-%The relation is built as follows: for each pair of state $s^1$, $s^3$, for each state 
-%$s^2$ such that $\mathcal{R}$ relates $s^1$ and $s^2$, and $\mathcal{R}'$ relates $s^2$ 
-%and $s^3$, we take the conjunction of the two predicates. The predicates for different 
-%values of $s^2$ are collected by a disjunction. 
-%Finally, a set of substitutions should ensure that the 
-%free variables of the predicates are only the ones of $\mathcal{T}_1$ and 
-%$\mathcal{T}_1$. These substitutions somehow express the different ways to match the two 
-%predicates by eliminating the 
-%free variables. We simplify the proof to the case where a single substitution is 
-%necessary for each state $s^2$; the extension to a set of substitution is relatively 
-%simple but complicates the notations. $\phi_p$ is this set of substitutions in the proof 
-%below.
-%
-% We will show
-%that $\mathcal{R}''$ is an FH-bisimulation. Consider 
-%$(s^1,s^3|\Pred\,'')\in\mathcal{R}''$. Then there is a set of states of 
-%$\mathcal{T}_2$ relating $s^1$ and $s^3$, let $(s^2_p)^{p\in P}$ be this family.  
-%For any $p\in P$ by definition of $\mathcal{R}''$,
-%$(s^1,s^2_p|\Pred_p)\in\mathcal{R}$,  and $(s^2_p,s^3|\Pred\,'_p)\in\mathcal{R}$. 
-%Additionally we have $\Pred\,'' = \bigvee_{p\in P} (\Pred_p\land\Pred_p)\,'\phi_p$.
-%We have 
-%the 
-%following by definition of bisimulation.
-%For any open transition $OT$ in $\mathcal{T}_1$ originating from $s^1$:
-%
-%\begin{mathpar}
-%
-%\inferrule*[myfraction=\reddottedrule]
-%{\{s^1_i\xrightarrow{a_i}_i {s^{1}}'_i\}^{i\in I_1}, % , s^1_i,s^{1'}_i\in
-%	%States(I_1)
-%	\{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
-%{s^1 \xrightarrow {v} {s^{1}}'}
-%
-%\end{mathpar}
-%
-%there exist open transitions $OT_{p x}^{x\in X} \subseteq \mathcal{T}_2$:
-%
-%\begin{mathpar}
-%
-%%    \left( fresh \ \set{a_i}, \set{b_j}, v_x.\ \
-%\inferrule*[myfraction=\reddottedrule]
-%{\{s^{2}_{pi}\xrightarrow{a_{p i x}}_i s^{2}_{p i x}\}^{i\in I_{2 p x}},
-%	\{\xrightarrow{b_{j p x}}_j\}^{j\in J_{2px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
-%{s^2_p \xrightarrow {v_{px}} s^{2}_{px}}
-%%         \right)
-%\end{mathpar}
-%
-%such that  $\forall x, J_1=J_{2px}, (s^{1'},s^{2}_{px}|\Pred_{target_{px}})\in 
-%\mathcal{R}$;
-%and  \\
-%
-%$\Pred_p \land \Pred_{OT}\\
-%\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-%\left( \forall j. b_j=b_{jpx}  \Rightarrow \Pred_{OT_{px}}
-%\land v\!=\!v_{px} \land
-%\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)$
-%
-%for any open transition $OT_{px}$, since
-%$(s^2_p,s^3|\Pred\,^\prime_p)\in\mathcal{R}'$ there exist open transitions
-%$OT_{pxy}^{x\in X, y\in Y} \subseteq \mathcal{T}_3$: 
-%
-%\begin{mathpar}
-%
-%%    \left( fresh \ \set{a_i}, \set{b_j}, v_x.\ \
-%\inferrule*[myfraction=\reddottedrule]
-%{\{s^{3}_i\xrightarrow{a_{i p x y}}_i s^{3}_{i p x y}\}^{i\in I_{3 p x y}},
-%	\{\xrightarrow{b_{j p x y}}_j\}^{j\in J_{3pxy}}, \Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
-%{s^3 \xrightarrow {v_{pxy}} s^{3}_{pxy}}
-%%         \right)
-%
-%\end{mathpar}
-%such that  $\forall y, J_{2px}=J_{3pxy}, 
-%(s^{2}_x,s^{3}_{pxy}|\Pred_{target_{pxy}})\in \mathcal{R}'$; and  \\
-%$\Pred\,'_p \land \Pred_{OT_{px}}\\
-%\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
-%\left( \forall j. b_{jpx}=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
-%\land v_{px}\!=\!v_{pxy} \land
-%\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.
-%
-%This is verified for each $p\in P$. Overall,  we have a family of open transitions 
-%$OT_{pxy}^{p\in 
-%P, x\in X, 
-%y\in Y} \subseteq \mathcal{T}_3$ that should simulate \emph{OT}.
-%
-%First, $\forall y, \forall x, \forall p, J_1=J_{2px}=J_{3pxy}, 
-%({s^{1}}',s^{3}_{pxy}|\Pred\,'_{target_{pxy}})\in \mathcal{R}''$. 
-%Indeed for any 
-%$p$, 
-%$x$, and 
-%$y$, $s^2_{px}$
-%relate ${s^{1}}'$ and $s^{3}_{pxy}$, indeed
-%$(s^{1'},s^{2}_{px}|\Pred_{target_{px}})\in \mathcal{R}$
-% and $(s^{2}_x,s^{3}_{pxy}|\Pred_{target_{pxy}})\in \mathcal{R}'$. 
-% More precisely, $s^{2}_{px} \in ({s^{2}_p}')^{p\in P'}$ where $({s^{2}_p}')^{p\in 
-% P'}$ 
-% is 
-% the set of states relating ${s^{1}}'$ and $s^{3}_{pxy}$.
-%Consequently, for all $p$, $x$, $y$,\\
-% $\left(\exists \phi'.\,(\Pred_{target_{px}}\land 
-%\Pred_{target_{pxy}})\phi'\land \fv((\Pred\land\Pred)\phi')\subseteq 
-%\fv(\mathcal{T}_1)\cup\fv(\mathcal{T}_3)\right)\implies 
-%\Pred\,'_{target_{pxy}}$ \\
-%This is one element of the  disjunction defining the 
-%predicate 
-%relating ${s^{1}}'$ and $s^{3}_{pxy}$ in the definition of $\mathcal{R}''$.
-%
-%Second, we need \\
-%\begin{small}
-%$\Pred\,'' \land \Pred_{OT}\\
-%\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
-%\left( \forall j. b_j=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
-%\land v\!=\!v_{pxy} \land
-%\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
-%\end{small}
-%
-%We have, for all $p$
-%\begin{small}
-%$\Pred_p \land \Pred_{OT}\land\Pred'_p\\
-%\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-%\left( \forall j. b_j=b_{jpx}  \Rightarrow \Pred_{OT_{px}}
-%\land v\!=\!v_{px} \land
-%\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\land\Pred'_p\\
-%%
-%\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-%\left( \forall j. b_j=b_{jpx}  \Rightarrow (\Pred_{OT_{px}}\land\Pred'_p)
-%\land v\!=\!v_{px} \land
-%\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\\
-%%
-%\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-%\big( \forall j. b_j=b_{jpx}  \Rightarrow (\bigvee_{y\in Y} 
-%\big( \forall j'. b_{j'px}=b_{j'pxy}  \Rightarrow \Pred_{OT_{pxy}}
-%\land v_{px}\!=\!v_{pxy}\\\hspace{3em}~ \land
-%\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\big))
-%\land v\!=\!v_{px} \land
-%\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\\
-%%
-%\hspace{1cm} \implies\!\!\! \bigvee_{x\in X} \bigvee_{y\in Y}
-%\big( \forall j, j'. b_j=b_{jpx} \land b_{j'px}=b_{j'pxy}
-%\Rightarrow \big( 
-%\Pred_{OT_{pxy}}
-%\land v\!=v_{px}\!=\!v_{pxy}\\\hspace{3em}~ \land
-%\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}
-% \land
-%\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\big)
-%$
-%
-%\end{small}
-%
-%Additionally, the Post substitutions only have an effect on the  predicates that  use 
-%some of the 
-%substituted 
-%variables, and because of the domain of the substitutions we have:\\
-%$(\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\land 
-%\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}})\phi\\
-%%
-%= 
-%(\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land
-%\Pred_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}) 
-%\phi\\
-%%
-%= 
-%((\Pred_{target_{px}}\land
-%\Pred_{target_{pxy}})\subst{\Post_{OT_{px}}}\phi) 
-%\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\\
-%%
-%\implies\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}
-%\subst{\Post_{OT_{pxy}}}\\
-% $
-%Finally, gathering the previous results, and using the fact that only variables of 
-%$\mathcal{T}_2$ are changed by $\phi$ substitutions:
-%
-%$\Pred\,'' \land \Pred_{OT}\\
-%\hspace{1cm} \implies\!\!\! \bigvee_{p\in P}(\Pred_p \land 
-%\Pred_{OT}\land\Pred\,'_p)\phi\\
-%\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
-%\left( \forall j. b_j=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
-%\land v\!=\!v_{pxy} \land
-%\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)
-%$
-%
-%This is the expected property.
-%
-%
-%\smallskip
-%Concerning the other direction of bisimulation, it is sufficient to notice that the role 
-%of $s^1$ and $s^3$ in the definition of $\mathcal{R}''$ is symmetrical, and thus the 
-%proof is similar.
-%
-%       \end{proof}
-%       
-%       \bigskip
-%       
-%       
-              \begin{proof}
-
-       	It is trivial to check reflexivity and symmetry. Here we focus on the
-       	transitivity. 
-       	To prove transitivity of strong FH-bisimulation on pNets it is sufficient to 
-       	prove 
-       	transitivity of the strong FH-bisimulation on states. Consider 3 open automata 
-       	$\mathcal{T}_1$, $\mathcal{T}_2$, $\mathcal{T}_3$ and states $s$, $t$, $u$ 
-       	in those 
-       	automata\footnote{We omit the constraints stating that each $s_x,\,t_x,\,u_x$ is 
-       	in the 
-       	states of 
-       		$\mathcal{T}_1,\,\mathcal{T}_2,\,\mathcal{T}_3$ for the sake of readability}.
-       	Suppose we have $\mathcal{R}$ an FH-bisimulation relation between states of 
-       	$\mathcal{T}_1$ and of  $\mathcal{T}_2$; members of $\mathcal{R}$ are of the form 
-       	$(s,t|\Pred_{s,t})$.
-       	Suppose we also  have $\mathcal{R}'$ an FH-bisimulation relation between states 
-       	of 
-       	$\mathcal{T}_2$ and of  $\mathcal{T}_3$; members of $\mathcal{R}'$ are of the 
-       	form 
-       	$(t,u|\Pred_{t,u})$.
-
-       	Let $\mathcal{R}''$ be the relation: 
-       	\[\mathcal{R}'' = 
-       	\{(s,u|\Pred_{s,u})\,\,\Big|\,\Pred_{s,u}=\hspace{-0.7cm}\bigvee_{\begin{array}{c}       		
-       		(s,t|\Pred_{s,t})\in\mathcal{R}\\ (t,u|\Pred_{t,u})\in\mathcal{R}' 	
-       		\end{array}
-       }\hspace{-0.5cm}\Pred_{s,t}\land\Pred_{t,u}\}\]
-
-This relation is the adaptation of the transitivity to the conditional relationship that 
-defines a bisimulation. Indeed the global disjunction together with the conjunction of 
-predicates plays exactly the role of the intermediate element in a transitivity rule: 
-``there exists an intermediate state'' corresponds to the global disjunction, and the 
-conjunction of states expresses the intermediate predicate is used to ensure 
-satisfiability of the predicate relating the first state to the last one.
-
-       	The relation is built as follows: for each pair of states $s$, $u$, for each 
-       	state 
-       	$t$ such that $\mathcal{R}$ relates $s$ and $t$, and $\mathcal{R}'$ relates 
-       	$t$ 
-       	and $u$, we take the conjunction of the two predicates. The predicates for 
-       	different 
-       	values of $t$ are collected by a disjunction.
-
-       	We will show
-       	that $\mathcal{R}''$ is an FH-bisimulation. Consider 
-       	$(s,u|\Pred_{s,u})\in\mathcal{R}''$. Then there is a set of states of 
-       	$\mathcal{T}_2$ relating $s$ and $u$, let $(t_p)^{p\in P}$ be this family.  
-       	       	We have $\Pred_{s,u} = \displaystyle{\bigvee_{p\in P} \Pred_{s,p}\land\Pred_{p,u}}$.
-
-\medskip
-
-       	For any $p\in P$ by definition of $\mathcal{R}''$,
-       	$(s,t_p|\Pred_{s,p})\in\mathcal{R}$,  and 
-       	$(t_p,u|\Pred\,'_{p,u})\in\mathcal{R}'$. 
-       	We have 
-       	the 
-       	following by definition of bisimulation:
-       	For any open transition $OT$ in $\mathcal{T}_1$ originating from $s$.
-       	\begin{mathpar}
-       	\openrule
-       	{
-       		\beta_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
-       	{s \OTarrow {\alpha} {s}'}     	
-       	\end{mathpar}
-
-       	There exist open transitions $OT_{p x}^{x\in X} \subseteq \mathcal{T}_2$:
-
-       	\begin{mathpar} 
-       	%    \left( fresh \ \set{a_i}, \set{b_j}, v_x.\ \
-       	\openrule
-       	{
-       		\beta_{j p x}^{j\in J_{px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
-       	{t_p \OTarrow {\alpha_{px}} t_{p x}}\qquad (*)
-       	%         \right)
-       	\end{mathpar}
-
-       	such that  $\forall x, J_1=J_{px}, (s',t_{px}|\Pred_{{px}})\in 
-       	\mathcal{R}$;
-       	and  \\
-
-       	$\Pred_{s,p} \land \Pred_{OT}\\
-       	\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}
-       	\left( \forall j. \beta_j=\beta_{jpx}  \land \Pred_{OT_{px}}
-       	\land \alpha\!=\!\alpha_{px} \land
-       	\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\right)}$\\
-
-For any open transition $OT_{px}$, since
-       	$(t_p,u|\Pred_{p,u})\in\mathcal{R}'$ there exist open transitions
-       	$OT_{pxy}^{y\in Y} \subseteq \mathcal{T}_3$:
-
-       	\begin{mathpar}  	
-       	%    \left( fresh \ \set{a_i}, \set{b_j}, v_x.\ \
-       	\openrule
-       	{
-       		\beta_{j p x y}^{j\in J_{pxy}}, 
-       		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
-       	{u \OTarrow {\alpha_{pxy}} u_{pxy}}\qquad (**)
-       	%         \right)    	
-       	\end{mathpar}
-       	such that  $\forall y, J_{px}=J_{pxy}, 
-       	(t_{px},u_{pxy}|\Pred_{{pxy}})\in \mathcal{R}'$; and  \\
-       	$\Pred\,'_{p,u} \land \Pred_{OT_{p x}}\\
-       	\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}\!
-       	\left( \forall j.\beta_{jpx}\!=\!\beta_{jpxy} \land\! \Pred_{OT_{pxy}}\!
-       	\land\! \alpha_{px}\!=\!\alpha_{pxy} \!\land\!
-       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}\!\uplus\!\Post_{OT_{pxy}}}\right)}$\\
-
-       	This is verified for each $p\in P$. Overall,  we have a family of open 
-       	transitions 
-       	$OT_{pxy}^{p\in 
-       		P, x\in X, 
-       		y\in Y} \subseteq \mathcal{T}_3$ that should simulate $OT$.
-
-       	First, we have $\forall y, \forall x, \forall p,  J_1=J_{px}=J_{pxy}, 
-       	({s}',u_{pxy}|\Pred\,'_{{pxy}})\in \mathcal{R}''$ for some $\Pred\,'_{{pxy}}$. 
-       	Indeed for any 
-       	$p$, 
-       	$x$, and 
-       	$y$, $t_{px}$
-       	relates ${s}'$ and $u_{pxy}$, we have
-       	$(s',t_{px}|\Pred_{{px}})\in \mathcal{R}$
-       	and $(t_{px},u_{pxy}|\Pred_{{pxy}})\in \mathcal{R}'$. 
-       	More precisely,  $t_{px} \in ({t'_p})^{p\in P'}$ where $({t'_p})^{p\in 
-       		P'}$\hl{$P'\subseteq P$} \TODO{NO : there is no relation between the two sets: they are not comparable} is 
-       	the set of states relating ${s}'$ and $u_{pxy}$ (the states used in the open transition must belong to the set of states ensuring the transitive relation).
-       	Additionally, for all $p$, $x$, $y$, $\Pred_{px}\land 
-       	\Pred_{{pxy}}\implies 
-       	\Pred\,'_{{pxy}}$ (this is one element of the  disjunction defining the 
-       	predicate $\Pred\,'_{{pxy}}$
-       	relating ${s}'$ and $u_{pxy}$ in the definition of $\mathcal{R}''$).
-
-One can notice that, as bisimulation predicates are used to relate states that 
-belong to two different open automata, the free variables of these predicates 
-that do not belong to the two related automata can safely be renamed to avoid any 
-name clash. In practice,
-we can suppose that $\Pred\,'_{{pxy}}$ does not 
-contain the variables of $\mathcal{T}_2$ because it is used to relate states of $\mathcal{T}_1$ and $\mathcal{T}_3$ .
-Indeed if $\Pred\,'_{{pxy}}$ uses variables of 	$\mathcal{T}_2$, we can consider instead another predicate that is equivalent to $\Pred\,'_{{pxy}}$ and does not
-contain the variables of 	$\mathcal{T}_2$ (this is safe according to the semantic interpretation of open automata and relations). 
-Similarly, we can suppose that $\Pred_{{px}}$ contains no 
-variable in $\mathcal{T}_3$, and $\Pred_{{pxy}}$ contains no 
-variable in $\mathcal{T}_1$.
-
-       	Second, by definition of bisimulation we need (recall that $\Pred_{s,u}$ is the 
-       	original predicate relating $s$ and $u$ by definition of the transitive 
-       	closure):\\
-       	\begin{small}
-       		$\Pred_{s,u} \land \Pred_{OT}\\
-       		\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
-       		\left( \forall j. \beta_j=\beta_{jpxy}  \land \Pred_{OT_{pxy}}
-       		\land \alpha\!=\!\alpha_{pxy} \land
-       		\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{pxy}}}\right)}$.
-       	\end{small}
-
-From (*) and (**) we have, for all $p$
-       	\begin{small}
-       		$\Pred_{s,p} \land \Pred_{OT}\land\Pred_{p,u}\\
-       		\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}
-       		\left( \forall j. \beta_j=\beta_{jpx}  \land \Pred_{OT_{px}}
-       		\land \alpha\!=\!\alpha_{px} \land
-       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\right)\land\Pred_{p,u}}\\
-       		%
-       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-       		\left( \forall j. \beta_j=\beta_{jpx}  \land 
-       		(\Pred_{OT_{px}}\land\Pred_{p,u})
-       		\land \alpha\!=\!\alpha_{px} \land
-       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\right)\\
-       		%
-       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-       		\big( \forall j. \beta_j=\beta_{jpx}  \land (\bigvee_{y\in Y} 
-       		\big( \forall j'. \beta_{j'px}=\beta_{j'pxy}  \land \Pred_{OT_{pxy}}
-       		\land \alpha_{px}\!=\!\alpha_{pxy}\\~\hspace*{2em}~ \land
-       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}\big))
-       		\land \alpha\!=\!\alpha_{px} \land
-       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\big)\\
-       		%
-       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X} \bigvee_{y\in Y}
-       		\big( \forall j, j'. \beta_j=\beta_{jpx} \land \beta_{j'px}=\beta_{j'pxy}
-       		\land \big( 
-       		\Pred_{OT_{pxy}}
-       		\land \alpha\!=\alpha_{px}\!=\!\alpha_{pxy}\\~\hspace*{2em}~ \land
-       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}
-       		\land
-       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\big)\big)
-       		$
-
-       	\end{small}
-
-By construction, four substitutions $\subst{~}$ only have an effect on the  
-variables of the open automaton they belong to, they also produce terms containing only 
-variables of the open automaton they belong to. Finally, because of the domain of the 
-substitutions of the predicates, we have:\\
-       	$\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\land 
-       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}\uplus
-       	\Post_{OT_{pxy}}}\Leftrightarrow\\ % we changed =
-       	\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}\land
-       	\Pred_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}\\
-       	\implies\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus
-       	\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}
-       	\Leftrightarrow\\ % we changed = 
-       	 \Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{pxy}}} $\\
-
-       	This allows us to conclude, with $\Pred_{s,u} = \bigvee_{p\in P} 
-       	\Pred_{s,p}\land\Pred_{p,u}$:
-
-      	\begin{small}     	
-$\displaystyle{\Pred_{s,u} \land \Pred_{OT}}\\
- \implies\!\!\! \bigvee_{p\in P} (
-	\Pred_{s,p}\land\Pred_{p,u} \land \Pred_{OT})\\
-\hspace{1cm} \implies\!\!\!\bigvee_{p\in P}
- \bigvee_{x\in X} \bigvee_{y\in Y}
-\big( \forall j, j'.\beta_j=\beta_{jpx} \land \beta_{j'px}=\beta_{j'pxy}
-\land \Pred_{OT_{pxy}}\\
-~\hspace*{2em}~\land \alpha\!=\!\alpha_{px}\!=\!\alpha_{pxy}\land\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus \Post_{OT_{pxy}}}\big)
-\\
-\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
-\left( \forall j. \beta_j\!=\!\beta_{jpxy}  \land \Pred_{OT_{pxy}}
-\land \alpha\!=\!\alpha_{pxy} \land
-\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{pxy}}}\right)$
-  \end{small}
-
-       	\smallskip
-       	Concerning the other direction of bisimulation, it is sufficient to notice that 
-       	the role 
-       	of $s$ and $u$ in the definition of $\mathcal{R}''$ is symmetrical, and thus 
-       	the 
-       	proof is similar.
-
-       \end{proof}
-
-\subsection{Composition Lemmas}       
-       The proofs of the composition theorems for FH-bisimulation rely on two main lemmas,
-dealing respectively with the decomposition of a composed behaviour
-between the context and the internal pNet, and with their recomposition.
-
-\subsubsection*{{\bf Lemma~\ref{lem-decompose}}: Open transition decomposition} ~\\
- Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$}.
-	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose:
-	\[ P[Q]_{j_0}  
-		\models
-		{\openrule
-			{
-				\beta_j^{j\in J}, \Pred,  
-				\Post}
-			{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
-				\ostate{s_i'^{\, i\in L}}}
-		}
-	\]
-		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.
-		 Then, there exist $\alpha_Q$, $\Pred\,'$, $\Pred\,''$, 
-		$\Post\,'$, $\Post\,''$ s.t.:\\[-2ex]
-		%\[
-		\begin{mathpar}
-		P\models{\openrule
-			{
-				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
-				\Pred\,',  
-				\Post\,'}
-			{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {\alpha}
-				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
-		}%\]
-	\vspace{-2.2ex}\\\text{and~~}
-		%\[
-		Q\models{\openrule
-			{
-				\beta_j^{j\in J\cap\Holes(Q)}, \Pred\,'',  
-				\Post\,''}
-			{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
-				\ostate{s_i'^{\,i\in L_Q}}}
-		}%\]
-		\end{mathpar}
-		and  $\Pred \iff \Pred\,'
-		\land \Pred\,''\land \alpha_Q=\beta_{j_0}$, $\Post=\Post\,'\uplus 
-		\Post\,''$ where $\Post\,''$ is the restriction of $\Post$ over variables  
-		$\vars(Q)$.
-
-\textbf{Preliminary note:}
-The introduction of fresh variables introduce alpha-conversion at many points 
-of the proof; we 
-	only 
-	give major arguments concerning alpha-conversion to make the proof readable; in 
-	general, fresh variables appear in each transition inside
-        terms $\beta_j$, $v$, and 
-	$\Pred$.
-
-   \begin{proof}
-
-Consider rule \TrDeux\ in 
-       Definition~\ref{def:operationalSemantics}, applied to the pNet $P[Q]_{j_0}$. 	
-	\noindent
-\begin{small}	
-\begin{mathpar}
-    \mprset {vskip=.8ex}
-\inferrule
-    {
-\Leaves(\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in 
-    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
-k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
-\\
-\\     	
-	\forall m\!\in\! I_1. {\pNet_m 
-	\models\openrule
-    	{
-    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
-    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
-    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
-  \qquad
-\forall m\!\in\! I_2.		{ \pNet_m 
-    	 \models
-    	\openrule
-    	{\emptyset, \Pred_m, \Post_m}
-    	{\ostate{s_m} \OTarrow {\alpha_m}
-    		\ostate{s_m'}} }\\\\
-     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
-    	\Pred = \bigwedge_{m\in I_1\uplus I_2}\!\! \Pred_m \land
-    	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2},\beta_j^{j\in J},\alpha)\\ 
-    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
-    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
-    }
-    {\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
-    	\models
-    	{\openrule
-    		{
-    		{\beta_j}^{j\in J^\prime}, \Pred,  \biguplus_{m\in I_1\uplus I_2} 
-    		\Post_m}
-    		{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
-    			\ostate{(s_i^\prime)^{i\in L}}}
-    	}
-    }\quad\TrDeux
-\end{mathpar}
-
-\end{small}
-%\begin{mathpar}
-%    \mprset {vskip=1ex}
-%\inferrule
-%    {
-%\Leaves(\mylangle \set{\pNet}, \set{\Sort}, \symb{SV}_k^{k\in 
-%    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
-%k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
-%\\
-%\\     	
-%	\forall m\!\!\in\!\! I_1. {\pNet_m 
-%	\models\openrule
-%    	{
-%    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
-%    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
-%    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
-%  \qquad
-%\forall m\!\!\in\!\! I_2.		{ \pNet_m 
-%    	 \models
-%    	\openrule
-%    	{\emptyset, \Pred_m, \Post_m}
-%    	{\ostate{s_m} \OTarrow {\alpha_m}
-%    		\ostate{s_m'}} }\\\\
-%     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
-%    	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
-%    	\Predsv(SV_k,\alpha_m^{m\in (I_1\uplus I_2)},\beta_j^{j\in J},\alpha)\\ 
-%    		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
-%    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
-%    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
-%    }
-%    {\mylangle \set{\pNet}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
-%    	\models
-%    	{\openrule
-%    		{
-%    		{\beta_j}^{j\in J^\prime}, \Pred, \uplus_{m\in I_1\uplus I_2} 
-%    		\Post_m}
-%    		{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
-%    			\ostate{(s_i^\prime)^{i\in L}}}
-%    	}
-%    }
-%\end{mathpar}
-
-We know each premise is \True\ for $P[Q]_{j_0}$. 
-  $j_0\in I_1$ because $Q$ is not a pLTS. We try to prove the equivalent premise for 
-$P$.
-
-First, $K$ and the synchronisation vector $SV_k$ are unchanged (however 
-$j_0$ passes from 
-the set of subnets to the set of holes). 
-%Then $SV=clone(\alpha_j^{j\in I_k\uplus\{j_0\}\uplus J_k})$.
-We have $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$.
-
-Now focus on the OTs of the subnets. For each $m\in I_1\uplus I_2$ we have one of the two 
-following OT:\\
-either $m$ in $I_1$
-\[
-\pNet_m \models\openrule
-    	{
-    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
-    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
-    		\ostate{(s_i^\prime)^{i\in L_m}}}\]
-or, $m$ in $I_2$
-\[{ \pNet_m 
-    	 \models
-    	\openrule
-    	{\emptyset, \Pred_m, \Post_m}
-    	{\ostate{s_m} \OTarrow {\alpha_m}
-    		\ostate{s_m'}}}\]
-
-Only elements of $(I_1\uplus I_2)\backslash\{j_0\}$   are useful to assert the premise for reduction of $P$; the last 
-one ensures the open transition for the pNet $Q$ (note that $Q$ is at place $j_0$, and by 
-definition of the open transition 
-for $P[Q]_{j_0}$, 
-$L_{j_0}=L_Q$, and $J_{j_0}=	J\cap\Holes(Q)$):\\[-2ex]
-	\[Q\models{\openrule
-		{
-			\beta_j^{j\in J\cap\Holes(Q)}, \Pred_{j_0},  
-			\Post\,''}
-		{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_{j_0}}
-			\ostate{(s_i')^{\, i\in L_Q}}}
-	}\]
-
-This already ensures the second part of the conclusion of the lemma, i.e. the OT for $Q$ 
-if we 
-choose  $\alpha_Q=\alpha_{j_0}$ and $\Pred\,''= \Pred_{j_0}$. 
-Considering 
-the OT of $P$ we have another  $J'$ that is $J'_p=J'\setminus\Holes(Q)\uplus 
-\{j_0\}$; we denote $I'_1=I_1\setminus \{j_0\}$ the predicate is 
-$\displaystyle{\Pred\,'=\!\!\!\!\!\bigwedge_{m\in I_1'\uplus I_2}\!\!\!\!\!\Pred_m  \land \Predsv(SV_k,\alpha_m^{m \in I'_1\uplus I_2},\beta_j^{j\in J\cup \{j_0\}},\alpha)}$
-where\footnotemark[\thefootnote] $\Predsv(SV_k,\alpha_m^{m \in I'_1\uplus I_2},\beta_j^{j\in 
-J\cup 
-\{j_0\}},\alpha)\Leftrightarrow 
-\forall i\in I'_1\uplus I_2.\, \alpha_i=\alpha'_i\land \forall j \in J\cup \{j_0\}.\, 
-\beta_j=\alpha'_j 
-\land 
-\alpha=\alpha'
-\land e_b$. Modulo renaming of fresh variables, this is identical to the predicate that 
-occurs in 
-the source open transition except $\alpha_{j_0}=\alpha'_{j_0}$ has been replaced by  
-$\beta_{j_0}=\alpha'_{j_0}$. As $\alpha_{j_0}=\alpha_Q$ and $\beta_{j_0}$ is free, we 
-have $\beta_{j_0}=\alpha'_{j_0}\land \beta_{j_0}=\alpha_Q \iff 
-\alpha_{j_0}=\alpha'_{j_0}$.
-Thus, $\Pred \iff (\Pred\,'
-		\land \Pred\,'')\land \alpha_Q=\beta_{j_0}$. 
-Finally, Post 
-%conditions are easily split\footnote{\TODO{moved. could
-%    even remove...?}Note that if the rules are not simplified, no
-%  post-condition range over the variables of $P$ and $Q$ at the same
-%  time} 
-into conditions of the context $P$ and the pNet $Q$ (they are
-builts similarly as they only deal with  
-leaves): $\Post=\Post\,'\uplus \Post\,''$. This concludes the 
-proof as we checked all the premises of the open transition for both $P$ and $Q$. We obtain the following reduction by the rule \TrDeux:
-	\noindent
-	\begin{small}
-\begin{mathpar}
-    \mprset {vskip=.8ex}
-\inferrule
-    {
-\Leaves(\mylangle {\pNet}_m^{m\in I\setminus\{j_0\}}, \set{\Sort}, \symb{SV}_k^{k\in 
-    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
-k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
-\\
-\\     	
-	\forall m\!\!\in\!\! I_1\setminus\{j_0\}. {\pNet_m 
-	\models\openrule
-    	{
-    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
-    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
-    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
-  \qquad
-\forall m\!\!\in\!\! I_2.		{ \pNet_m 
-    	 \models
-    	\openrule
-    	{\emptyset, \Pred_m, \Post_m}
-    	{\ostate{s_m} \OTarrow {\alpha_m}
-    		\ostate{s_m'}} }\\\\
-     J' = \biguplus_{m\in I_1 \setminus \{j_0\}}\!\! J_m \uplus J 	\\
-    	\Pred\,' = \bigwedge_{m\in I_1\uplus I_2\setminus\{j_0\}}\!\! \Pred_m \land
-    	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2 \setminus \{j_0\}},\beta_j^{j\in J\cup\{j_0\}},\alpha)\\ 
-    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1\setminus\{j_0\}}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
-    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
-    }
-    {\mylangle {\pNet}_m^{m\in I\setminus\{j_0\}}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
-    	\models
-    	{\openrule
-    		{
-    		{\beta_j}^{j\in J\setminus \Holes(Q)\uplus \{j_0\}}, \Pred\,',  \biguplus_{m\in I_1\setminus\{j_0\}\uplus I_2} 
-    		\Post_m}
-    		{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {\alpha}
-    			\ostate{(s_i^\prime)^{i\in L\setminus L_Q}}}
-    	}
-    }
-\end{mathpar}
- \end{small}
-\end{proof}
-
-In general, the actions that can be emitted by $Q$ is  a subset of the possible 
-actions of the holes, and the predicate involving $v_Q$ and the synchronisation vector is 
- more restrictive than the one involving only the variable $\beta_{j_0}$. This has no 
- impact 
- on the previous proof and this restriction  results from the composition of predicates.
-%\TODO{is this useful? = yes, I think }
-
-\subsubsection*{ \bf{Lemma~\ref{lem-compose}}:  Open transition composition}~\\
-	Consider two pNets $P$ and $Q$ where $P$ is not a pLTS. Suppose $j_0\in J$ and:\\[-1ex]
-\begin{mathpar}
-%\[
-P\models{\openrule
-	{
-		\beta_j^{j\in J}, 
-		\Pred,  
-		\Post}
-	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
-		\ostate{s_i'^{\, i\in L}}}
-}%\]
-\text{~~\qquad\qquad~and~\qquad\qquad~~}
-%\[
-Q\models{\openrule
-	{
-		\beta_j^{j\in J_Q},
-		 \Pred\,',  
-		\Post\,'}
-	{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
-		\ostate{s_i'^{\, i\in L_Q}}}
-}%\]
-\end{mathpar}
-Then, we have:\\[-2ex]
-	\[ P[Q]_{j_0}  
-	\models
-	{\openrule
-		{
-			\beta_j^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
-			\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0},  
-			\Post\uplus \Post\,'}
-		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {\alpha}
-			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
-	}
-	\]
-
-Note that this does not mean that any two pNets can be composed and produce an open 
-transition. Indeed, the predicate $\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0}$ will not 
-be satisfiable if the action of $\alpha_Q$ cannot be matched with $\beta_{j_0}$.
-Note also that $\beta_{j_0}$ is now only used as an intermediate term inside formulas: it 
-does not appear neither as global action nor as an action of a hole.
-
-\begin{proof} 
-Let $P=\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle$.
-Consider first the open transition derived from $P$.
-       Consider each premise of the open transition (constructed by \TrDeux\ in 
-Definition~\ref{def:operationalSemantics}). 
-	\begin{small}
-\begin{mathpar}
-    \mprset {vskip=.8ex}
-\inferrule
-    {
-\Leaves(\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in 
-    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
-k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
-\\
-\\     	
-	\forall m\!\in\! I_1. {\pNet_m 
-	\models\openrule
-    	{
-    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
-    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
-    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
-  \qquad
-\forall m\!\in\! I_2.		{ \pNet_m 
-    	 \models
-    	\openrule
-    	{\emptyset, \Pred_m, \Post_m}
-    	{\ostate{s_m} \OTarrow {\alpha_m}
-    		\ostate{s_m'}} }\\\\
-     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
-    	\Pred = \bigwedge_{m\in I_1\uplus I_2}\!\! \Pred_m \land
-    	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2},\beta_j^{j\in J},\alpha)\\ 
-    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
-    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
-    }
-    {\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
-    	\models
-    	{\openrule
-    		{
-    		{\beta_j}^{j\in J^\prime}, \Pred,  \biguplus_{m\in I_1\uplus I_2} 
-    		\Post_m}
-    		{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
-    			\ostate{(s_i^\prime)^{i\in L}}}
-    	}
-    }\quad \TrDeux
-\end{mathpar}  
-\end{small}
-We know each premise is \True\ for $P$ and try to prove the equivalent premise for 
-$P[Q]_{j_0}$ (using the open transition of $Q$). $P[Q]_{j_0}$ exhibits a similar \TrDeux~rule where
-$K$ and the synchronisation vector are unchanged ($j_0$ is now in the set of sub-pNets); 
-$SV_k=\SV{(\alpha'_j)^{j\in I\uplus\{j_0\}\uplus 
-	J}}{\alpha'}{e_b}$. $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$. $I$ and $J$ 
-	are the 
-    set of leaves and holes of $P$, $I_1\uplus I_2$ and $J'$ are the sets of moving 
-    leaves and holes 
-    in the reduction of $P$. All sub-pNets of 
-    must
-    be 
-reduced, we need:%\footnote{again we skip arguments related to renaming of fresh 
-%variables}:
-\[
-    	\forall m\!\in\! I_1\uplus\{j_0\}. {\pNet_m 
-    	\models\openrule
-    	{
-    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
-    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
-    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
-  \]\[
-\forall m\!\in\! I_2.		{ \pNet_m 
-    	 \models
-    	\openrule
-    	{\emptyset, \Pred_m, \Post_m}
-    	{\ostate{s_m} \OTarrow {\alpha_m}
-    		\ostate{s_m'}} }\]
-%\forall m\!\!\in\!\! I\cup \{j_0\}. 	
-%    {\left(\begin{array}{l}
-%	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
-%    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m},
-%    	\{\xrightarrow{\beta_{j}}_j\}^{j\in J_m}, \Pred_m, \Post_m}
-%    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
-%    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
-%		{ \pNet_m 
-%    	 \models
-%    	\inferrule*[myfraction=\reddottedrule]
-%    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
-%    	{\ostate{s_m} \OTarrow {v_m}
-%    		\ostate{s_m'}} \land I_m=\{m\} \land J_m=\emptyset}
-%\end{array}\right)}\]
-the sub-pNet at position $j_0$ is the one filled by $Q$ (we define $P_{j_0}=Q$ and similarly $J_m=J_Q$, $\Pred_m=\Pred\,'$, $\Post_m=\Post\,'$,\ldots are the elements of the OT of Q) which offers an open transition
-by hypothesis, the other open transitions are immediate consequence of the open 
-transition that can be performed by $P$ (premises of \TrDeux).
-The set of moving leaves is the union of the moving leaves in the open transition for $P$ 
-and the ones for $Q$; similarly the moving holes are the union of the moving 
-holes, minus $j_0$: $J'_{PQ}=  J\setminus\{j_0\}\uplus J_Q$. The 
-predicate for the open 
-transition is:\\
- $\displaystyle{\Pred\,''=\!\!\!\!\bigwedge_{m\in I _1\uplus I_2}\!\!\!\Pred_m \land \Pred\,'
-\land \Pred(SV_k,v_i^{i\in I_1\uplus I_2}\uplus(j_0\mapsto v_Q),\beta_j^{j\in 
-J},\alpha)}$. \\
-By definition we have:\\
-$\Pred(SV_k,\alpha_i^{i\in I}\uplus(j_0\mapsto \alpha_Q),\beta_j^{j\in 
-J},v)\Leftrightarrow
-	\forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, \beta_j=\alpha'_j \land 
-	\alpha=\alpha'\land \alpha_Q=\alpha_{j_0}\land e_b$,
-this is equivalent to $\forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, 
-\beta_j=\alpha'_j \land 
-	\alpha=\alpha'\land \alpha_Q=\beta_{j_0}\land \beta_{j_0}=\alpha_{j_0}\land e_b$
- and by definition of $\Pred$ (as obtained by \TrDeux),
-	$\Pred\,''\iff \Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0}$. The post-condition 
-	gathers the post-conditions related to all 
-	the leaves: $\displaystyle{\biguplus_{m\in I_1\cup\{j_0\}\uplus I_2} 
-    		\!\!\!\!\!\Post_m = 	\Post\uplus \Post\,'}$.\\ Finally, the composed open transition can be
-        built by \TrDeux\ as follows
-	\noindent
-	\begin{small}
-\begin{mathpar}
-    \mprset {vskip=.8ex}
-\inferrule
-    {
-\Leaves(\mylangle {\pNet}_m^{m\in I\cup\{j_0\}}, \set{\Sort}, \symb{SV}_k^{k\in 
-    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
-k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
-\\
-\\     	
-	\forall m\!\!\in\!\! I_1\cup\{j_0\}. {\pNet_m 
-	\models\openrule
-    	{
-    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
-    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
-    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
-  \qquad
-\forall m\!\!\in\!\! I_2.		{ \pNet_m 
-    	 \models
-    	\openrule
-    	{\emptyset, \Pred_m, \Post_m}
-    	{\ostate{s_m} \OTarrow {\alpha_m}
-    		\ostate{s_m'}} }\\\\
-     J'_{PQ}=  J\setminus\{j_0\}\uplus J_Q	\\
-    	\Pred\,'' =\bigwedge_{m\in I _1\uplus I_2}\Pred_m \land \Pred\,'
-\land \Pred(SV_k,v_i^{i\in I_1\uplus I_2}\uplus(j_0\mapsto v_Q),\beta_j^{j\in 
-J},\alpha)\\ 
-    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1\cup\{j_0\}}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
-    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
-    }
-    {\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
-    	\models
-    	{\openrule
-    		{
-    		{\beta_j}^{j\in  J'_{PQ}}, \Pred\,'',  	\Post\uplus \Post\,'}
-    		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {\alpha}
-    			\ostate{(s_i^\prime)^{i\in L\uplus L_Q}}}
-    	}
-    }
-\end{mathpar}  
-\end{small}
-   This provides the desired conclusion.     \end{proof}
-
-Note that we also have the following lemma (trivial):
-
-\begin{lemma}[Open transition composition -- inactive]\label{lem-compose-2} ~\\	This lemma is the simple case where the pNet filling the hole is not involved in the transition.
-Suppose $j_0\not\in J$ and $L_Q=\Leaves({Q})$:\\[-2ex]
-\begin{mathpar}
-%\[
-P\models{\openrule
-	{
-		\beta_j^{j\in J}, 
-		\Pred,  
-		\Post}
-	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
-		\ostate{s_i'^{\, i\in L}}}
-}%\]
-\end{mathpar}
-Then, for any state $\ostate{s_i^{i\in L_Q}}$ of $Q$, we have\\[-1ex]
-	\[ P[Q]_{j_0}  
-	\models
-	{\openrule
-		{
-			\beta_j^{j\in J}, 
-			\Pred,  
-			\Post}
-		{\ostate{s_i^{i\in L}\uplus s_i^{i\in L_Q}} \OTarrow {\alpha}
-			\ostate{s_i'^{\, i\in L}\uplus s_i^{i\in L_Q}}}}
-	\]
-\end{lemma}
-The proof is trivial.
-
- \subsection{Proof of Theorem ~\ref{thm-congr-eq}}
-\noindent{\bf  Congruence}:
-\textit{	Consider an open pNet:
-	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
-	\set{\symb{SV}}\myrangle$.
-	Let $j_0\in J$ be a hole. Let $\pNetQ$ and $\pNetQ'$ be two FH-bisimilar pNets such that 
-	$\Sortop(\pNetQ)=\Sortop(\pNetQ')=\Sort_{j_0}$\footnote{Note that $\Sortop(\pNetQ)=\Sortop(\pNetQ')$ is 
-	ensured by 
-	strong bisimilarity.}. Then 
-	$\pNet[\pNetQ]_{j_0}$ and 
-	$\pNet[\pNetQ']_{j_0}$ are FH-bisimilar.
-}
-\medskip
-\begin{proof}
- The proof of Theorem~\ref{thm-congr-eq} exhibits classically a bisimulation relation for 
- a 
- composed system.  It considers then an open transition of $P[Q]_{j_0}$ that should be 
- simulated. It then uses  Lemma~\ref{lem-decompose} to decompose the open transition 
- of $P[Q]_{j_0}$ and obtain an open transition of $P$ and $Q$; the FH-bisimulation 
- property can 
- be applied  to $Q$ to obtain an equivalent family of open transitions of $Q'$; this 
- family is 
- then recomposed by Lemma~\ref{lem-compose} to build a set of open transitions of 
- $P[Q']_{j_0}$ 
- that will simulate the original one.
-
- Let $\Leaves(Q)=p_l^{l\in L}$, $\Leaves(Q')={p'}_l^{l\in L'}$, 
- $\Leaves(P)=p_l^{l\in L_P}$.
- Consider $Q$ FH-bisimilar to $Q'$. It means that there is a relation 
- $\mathcal{R}$ that is an FH-bisimulation between the open automata of the two pNets. 
- We will consider the relation
-%\footnote{$\uplus$ is defined on sets as the disjoint union 
-% of the contained indexed 
-% sets} 
-$\mathcal{R}'=\{(s,t|\Pred_{s,t})|s=s'\uplus s'' \land 
- t=t'\uplus s'' \land s''\in \mathcal{S}_P \land (s',t'|\Pred_{s,t})\in\mathcal{R}\}$ 
-   where $\mathcal{S}_P$ is the set of states of the open automaton of $P$.	We will prove 
- that $\mathcal{R}'$ is an open FH-bisimulation. Consider a pair of FH-bisimilar 
- states: $(\ostate{s_{i}^{i \in L_P\uplus L}},\ostate{{t}_{i}^{i \in L'}\uplus 
- 	{s}_{i}^{i \in L_P}}|\Pred_{s,t})\in\mathcal{R}'$. %Those are states of the open 
- %	automata of 
- %	the pNets $P[Q]_{j_0}$ and $P'[Q]_{j_0}$. 
- Consider an 
- open transition $OT$ of $P[Q]_{j_0}$. %We need to find a family ${OT}_x^{x\in X}$ of 
- %	open transitions of $P'[Q]_{j_0}$ that satisfy the conditions of
- %	Definition~\ref{def-FH-bisim}. $OT$ is of the form 
- \\[-2ex]     
- \[P[Q]_{j_0}\models\openrule
- {
- 	\beta_j^{j\in J},\Pred_{OT},\Post_{OT}}
- { \ostate{s_{i}^{i \in L_P\uplus L}}\OTarrow {\alpha} \ostate{{s'}_{i}^{~i \in 
- 			L_P\uplus 
- 			L}}}\]
- Let $J'=J\setminus \Holes(Q) \cup \{j_0\}$.	 By 
- Lemma~\ref{lem-decompose} we have :\\[-2ex]
- 	\begin{mathpar}
- P\models{\openrule
- 	{
- 		\beta_j^{j\in J'}, 
- 		\Pred\,',  
- 		\Post\,'}
- 	{\ostate{s_{i}^{i\in L_P}} \OTarrow {\alpha}
- 		\ostate{s_{i}'^{\,i\in L_P}}}
- }\\
- Q\models{\openrule
- 	{
- 		\beta_j^{j\in J\cap\Holes(Q)}, \Pred\,'',  
- 		\Post\,''}
- 	{\ostate{s_{i}^{i\in L}} \OTarrow {\alpha_Q}
- 		\ostate{s_{i}'^{\,i\in L}}}
- }\end{mathpar}
- and  $\Pred_{OT}\iff \Pred\,'
- \land \Pred\,''\land \alpha_Q= \beta_{j_0}$, $\Post_{OT}=\Post\,'\uplus 
- \Post\,''$ ($\Post\,''$ is the restriction of $\Post$ over $\vars(Q)$). As $Q$ is FH-bisimilar to $Q'$ and $(\ostate{s_{i}^{i \in 
- 		L}},\ostate{{t}_{i}^{i \in L'}}|\Pred_{s,t})\in\mathcal{R}$ there is a family 
- $OT'_x$ 
- of 	open transitions of the automaton of $Q'$ such that\\[-2ex] 
- \begin{mathpar}
- Q'\models\openrule
- {
- 	\beta_{j x}^{j\in J\cap\Holes(Q)}, 
- 	\Pred_{OT_x},\Post_{OT_x}}
- {\ostate{t_{i}^{i\in L'}} \OTarrow {\alpha_x} \ostate{t_{i x}^{i\in L'}}}
- \end{mathpar}
- and  $\forall x, (\ostate{s_{i}^{i\in L}},\ostate{t_{i x}^{i\in 
- 		L'}}|\Pred_{s x})\in 
- \mathcal{R}$; 
- and  \\
- $\Pred_{s,t} \land \Pred\,''
- \implies$\\ $\displaystyle{\bigvee_{x\in X}
- \left( \forall j\in J\cap \Holes(Q). \beta_j\!=\!\beta_{jx}\!  \land\! 
- \Pred_{OT_x}
- \land \alpha_Q\!=\!\alpha_x \land  
- \Pred_{s, x}\subst{\Post\,''\uplus\Post_{OT_x}}\right)}$
-
- We can now apply Lemma~\ref{lem-compose} on each of the $OT'_x$ together with 
- the transition of $P$ and obtain a new family $OT_x$ of open transitions (where for 
- $i\in L_P$, $t_{i}=s_{i}$ and $t_{i x}=s'_{i}$, and for $j\in Holes(P)$, 
- $\beta_{j x}=\beta_j$):\\[-2ex]
- \[ P[Q']_{j_0}  
- \models
- {\openrule
- 	{
- 		\beta_{j x}^{j\in J}, 
- 		\Pred\,'\land\Pred_{OT_x}\land \alpha_x=\beta_{j_0 x} ,  
- 		\Post\,'\uplus \Post_{OT_x} }
- 	{\ostate{t_{i }^{i\in L'\uplus L_Q}} \OTarrow {\alpha_x}
- 		\ostate{{t}_{i x}^{i\in L'\uplus L_Q}}}
- }
- \]
-
- Observe that we used the fact that $J=(J\setminus\Holes(Q)\cup 
- \{j_0\})\setminus\{j_0\}\cup 
- (J\cap\Holes(Q))$. Now we have to verify the conditions for the 
- FH-bisimulation between $OT$ and $OT_x$.
- $\forall x, (\ostate{{s'}_{i}^{~i\in L_P\uplus L}},\ostate{t_{i 	x}^{i\in L_P\uplus L'}}|\Pred_{s, x})\in 
- \mathcal{R}'$ (by definition of
- $\mathcal{R}'$) and in three steps we get:
-
- \noindent                        
- \begin{small} $\Pred_{s,t} \land \Pred_{OT} 
- \implies 	\Pred_{s,t}\land\Pred\,'\land \Pred\,''\land\alpha_Q=\beta_{j_0}\\ % 
- 	%reversed 
- 	%substitution 
- 	\implies  \hspace{-2ex}
- 	{\displaystyle\bigvee_{x\in X}
- 	\left( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \land 
- 	\Pred_{OT_x}
- 	\land \alpha_Q\!=\!\alpha_x \land  
- 	\Pred_{s,x}\subst{\Post\,''\uplus\Post_{OT_x}}\right)\land
- }
- \\ \Pred\,'\land\alpha_Q=\beta_{j_0} \\
- 	\implies
- 	 \hspace{-2ex}
- 	{\displaystyle\bigvee_{x\in X}
- 		( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \land 
- 		\Pred\,'\land \Pred_{OT_x}
- 		\land \alpha_Q\!=\!\alpha_x \land \alpha_Q\!=\!\beta_{j_0 x}\, \land} \\ 
- 		\Pred_{s, x}\subst{\Post\,''\uplus\Post_{OT_x}})
- 	 $\end{small}
-
- Note that, $\beta_{j_0}$ can be transformed into  $\beta_{j_0 x}$ because of the 
- implication hypothesis.
- %\TODO{There was a confusion between the $\Rightarrow$ between the
- %  steps, and the $\implies$ inside the formulas...}
-% 
-% Explanations: first, we reversed the substitution; then we
-% restricted the 
-% substitution as $\beta_{j_0}$ only appears in $\Pred\,'$; then we
-% applied the property of FH-bisimulation for $P$ and rearranged the
-% terms using the fact that $v_Q=v_x$.
- The obtained formula reaches the goal except for 
- two points:
- \begin{itemize}
- 	\item We need $\forall j\!\in\! J$ instead of $\forall j\!\in\! J\cap\Holes(Q)$  but  
- 	adding prerequisite on more variables 
- 	does not   	change the validity of the formula (those variables are not used).
- 	\item Concerning the last term, we need 
- 	$\Pred_{s x}\subst{\Post_{OT}\uplus(\Post\,'\uplus \Post_{OT_x})}$, i.e.
- 	$\Pred_{s, x}\subst{(\Post\,'\uplus 	\Post\,'')\uplus(\Post\,'\uplus \Post_{OT_x})}$. We 
- 	can conclude by observing that	$\Pred_{s,x}$ does not use any variable of $P$ 
- 	and thus the substitution $\subst{Post\,'}$ has no effect on it.
- \end{itemize}	
-Finally: \\
-\begin{small} $\Pred_{s,t} \land \Pred_{OT} \implies\\
-{\displaystyle\bigvee_{x\in X}
- 		\!\left( \forall j\in J. \beta_j=\beta_{jx} \! \land\! 
- 		\big(\Pred\,'\land\! \Pred_{OT_x}
- 		 \land \alpha_Q\!=\!\beta_{j_0 x}\right)\! \land\! \alpha_Q\!=\!\alpha_x\land\!  \Pred_{s, x}\subst{\Post\,''\!\uplus\!\Post_{OT_x}}\big)
- 		}$
- 		\end{small}\\
-This proves the  condition of the FH-simulation, the other direction is 
- similar.
-\end{proof}
-
-        \subsection{Proof of Theorem ~\ref{thm-ctxt-eq}: Context equivalence}
-\textit{	Consider two FH-bisimilar open pNets:
-	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
-	\set{\symb{SV}}\myrangle$ and 	$\pNet' = \mylangle {\pNet'}_i^{i\in I}, 
-	\Sort_j^{j\in 
-	J}, 	\set{\symb{SV'}}\myrangle$ 
-	(recall they must have the same holes to be bisimilar).
-	Let $j_0\in J$ be a hole, and $Q$ be a pNet such that $\Sortop(Q)=\Sort_{j_0}$. Then 
-	$\pNet[Q]_{j_0}$ and 
-	$\pNet'[Q]_{j_0}$ are FH-bisimilar.
-}
-
-\medskip
-
-\begin{proof}
-The proof of Theorem~\ref{thm-ctxt-eq} exhibits  a bisimulation relation for a 
-composed system. It then uses  Lemma~\ref{lem-decompose} to decompose the open transition 
-of $P[Q]_{j_0}$ and obtain an open transition of $P$ on which the FH-bisimulation 
-property can 
-be applied  to obtain an equivalent family of open transitions of $P'$; this family is 
-then recomposed by Lemma~\ref{lem-compose} to build a set of open transitions of 
-$P'[Q]_{j_0}$ 
-that will simulate the original one.
-
-        Let $\Leaves(Q)=p_l^{l\in L_Q}$, 
-$\Leaves(P)=p_l^{l\in L}$, $\Leaves(P')={p'}_l^{l\in L'}$.
-	Consider $P$ FH-bisimilar to $P'$. It means that there is a relation 
-	$\mathcal{R}$ that is an FH-bisimulation between the open automata of the two pNets. 
-	We will consider the relation $\mathcal{R}'=\{(s,t|\Pred_{s,t})|s=s'\uplus s'' \land 
-	t=t'\uplus s'' \land s\in \mathcal{S}_Q \land (s',t'|\Pred_{s,t})\in\mathcal{R}\}$ 
-	where $\mathcal{S}_Q$ is the set of states of the open automaton of $Q$.	We will prove 
-	that $\mathcal{R}'$ is an open FH-bisimulation. Consider a pair of FH-bisimilar 
-	states: $(\ostate{s_{1 i}^{i \in L\uplus L_Q}},\ostate{{s}_{2 i}^{i \in L'}\uplus 
-	{s}_{1 i}^{i \in L_Q}}|\Pred)\in\mathcal{R}'$. %Those are states of the open 
-%	automata of 
-%	the pNets $P[Q]_{j_0}$ and $P'[Q]_{j_0}$. 
-Consider an 
-	open transition $OT$ of $P[Q]_{j_0}$. %We need to find a family ${OT}_x^{x\in X}$ of 
-%	open transitions of $P'[Q]_{j_0}$ that satisfy the conditions of
-%	Definition~\ref{def-FH-bisim}. $OT$ is of the form 
-\\[-2ex]     
-	\[P[Q]_{j_0}\models\openrule
-	{
-		\beta_j^{j\in J},\Pred_{OT},\Post_{OT}}
-	{ \ostate{s_{i}^{i \in L\uplus L_Q}}\OTarrow {\alpha} \ostate{{s'}_{i}^{~i \in 
-	L\uplus 
-	L_Q}}}\]
-Let $J'=J\setminus \Holes(Q) \cup \{j_0\}$.	 By 
-	Lemma~\ref{lem-decompose} we have :\\[-2ex]
-			\begin{mathpar}
-				P\models{\openrule
-				{
-					\beta_j^{j\in J'}, 
-					\Pred\,',  
-					\Post\,'}
-				{\ostate{s_{1}^{i\in L}} \OTarrow {\alpha}
-					\ostate{s_{i}'^{~ i\in L}}}
-			}\\
-			Q\models{\openrule
-				{
-					\beta_j^{j\in J\cap\Holes(Q)}, \Pred\,'',  
-					\Post\,''}
-				{\ostate{s_{i}^{i\in L_Q}} \OTarrow {\alpha_Q}
-					\ostate{s_{i}'^{~ i\in L_Q}}}
-			}\end{mathpar}
-			and  $\Pred_{OT} \iff \Pred\,'
-		\land \Pred\,''\land \alpha_Q=\beta_{j_0}$, $\Post_{OT}=\Post\,'\uplus 
-			\Post\,''$ ($\Post\,''$ is the restriction of $\Post$ over $\vars(Q)$). As $P$ is FH-bisimilar to $P'$ and $(\ostate{s_{i}^{i \in 
-			L}},\ostate{{t}_{i}^{i \in L'}}|\Pred_{s,t})\in\mathcal{R}$ there is a family 
-			$OT'_x$ 
-			of 	open transitions of the automaton of $P'$ such that\\[-2ex] 
-			\begin{mathpar}
-			%    \left( fresh \ \set{a_i}, \set{b_j}, v_x.\ \
-			P'\models\openrule
-			{
-				\beta_{j x}^{j\in J'}, 
-				\Pred_{OT_x},\Post_{OT_x}}
-			{\ostate{t_{i}^{i\in L'}} \OTarrow {\alpha_x} \ostate{t_{i x}^{i\in L'}}}
-			%         \right)
-			\end{mathpar}
-			and  $\forall x, (\ostate{s_{i}^{i\in L}},\ostate{t_{i x}^{i\in 
-			L'}}|\Pred_{s x})\in 
-			\mathcal{R}$; 
-			and  \\
-			$\displaystyle{\Pred_{s,t} \land \Pred\,'
-		 \!\!\implies\!\!\! \bigvee_{x\in X}\!
-			\left( \forall j\in J'. \beta_j=\beta_{jx}\!  \land\! 
-			\Pred_{OT_x}\!
-			\land\! \alpha\!=\!\alpha_x\! \land\!  
-			\Pred_{s,x}\subst{\Post\,'\uplus\Post_{OT_x}}\right)}$
-			%     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x}) \right)$.
-
-			We can now apply Lemma~\ref{lem-compose} on each of the $OT'_x$ together with 
-			the transition of $Q$ and obtain a new family $OT_x$ of open transitions (where for 
-			$i\in L_Q$, $t_{i}=s_{i}$ and $t_{i x}=s'_{i}$, and for $j\in Holes(Q)$, 
-			$b_{j x}=b_j$):\\[-2ex]
-				\[ P'[Q]_{j_0}   
-				\models
-				{\openrule
-					{
-						\beta_{j x}^{j\in J}, 
-						\Pred_{OT_x} \land\Pred\,''\land\alpha_Q=\beta_{j_0 x},  
-						\Post_{OT_x}\uplus \Post\,''}
-					{\ostate{t_{ i }^{i\in L'\uplus L_Q}} \OTarrow {\alpha_x}
-						\ostate{{t}_{ i x}^{i\in L'\uplus L_Q}}}
-				}
-				\]
-			Observe that $J=(J\setminus\Holes(Q)\cup \{j_0\})\setminus\{j_0\}\cup 
-			(J\cap\Holes(Q))$. Now we have to verify the conditions for the 
-			FH-bisimulation between $OT$ and $OT_x$.
-			 $\forall x, (\ostate{{s'}_{i}^{~i\in L\uplus L_Q}},\ostate{t_{i 
-			x}^{~i\in L'\uplus L_Q}}|\Pred_{s, x})\in 
-			\mathcal{R}'$ (by definition of
-                        $\mathcal{R}'$) and in four steps we get:
-
-\noindent                        
-\begin{small} 
-$\Pred_{s,t} \land \Pred_{OT} \implies
- \Pred_{s,t}\land\Pred\,'\land \Pred\,''\land \alpha_Q=\beta_{j_0}\\  
- \implies  \hspace{-2ex}
-{\displaystyle{\bigvee_{x\in X}\!(\forall j\!\in\! J'. \beta_j\!=\!\beta_{jx}  
-\!\land \!
-\Pred_{OT_x}\!\land\! \alpha_Q\!=\!\beta_{j_0}
-\land\! \alpha\!=\!\alpha_x}} %\\ \hspace*{40mm} %
-\land \Pred_{s, x}\subst{\Post\,'\uplus\Post_{OT_x}}) \land
-\Pred\,''\\ % 
-			%FH for P
- \implies  \hspace{-2ex}
-	{\displaystyle{\bigvee_{x\in X}\!(\forall j\!\in\! J'. \beta_j\!=\!\beta_{jx}  
-\land \!
-\left(\Pred_{OT_x}\!\land\!
-\Pred\,''\!
-\land \alpha_Q\!=\!\beta_{j_0 x}\right)
-\land \alpha\!=\!\alpha_x}} 
-\land \Pred_{s,x}\subst{\Post\,'\uplus\Post_{OT_x}}) 	
-$\end{small}
-
-%\TODO{There was a confusion between the $\Rightarrow$ between the
-%  steps, and the $\implies$ inside the formulas...}
-
- The obtained formula reaches the goal except for two points:
-\begin{itemize}
-	\item We need $\forall j\!\in\! J$ instead of $\forall j\!\in\! J'$ with 
-	$J'\!=\!J\!\setminus\! \Holes(Q) \cup \{j_0\}$ but the formula under the quantifier 
-	does not depend on 
-	$b_{j_0}$ now (thanks to 
-	the substitution). Concerning $\Holes(Q)$, adding prerequisite on more variables 
-	does not 
-	change the validity of the formula (those variables are not used).
-	\item We need $\Pred_{s, x}\subst{\Post_{OT}\uplus(\Post_{OT_x}\uplus \Post\,'')}$, i.e.,
-	$\Pred_{s,x}\subst{(\Post\,'\uplus \Post\,'')\uplus(\Post_{OT_x}\uplus \Post\,'')}$. We 
-	can conclude by observing that	$\Pred_{s, x}$ does not use any variable of $Q$ 
-	and thus the substitution involving $\Post\,''$ has no effect.
-\end{itemize}	
-This proves the  condition of the FH-simulation, the other direction is 
-similar.
-\end{proof}
-
-       \section{Weak FH-bisimulation lemmas and proofs}
-
-We  define a quantified composition operator for effects, i.e. $\Post$ elements of the open transitions.
-We use ${\displaystyle \bigotimes_{i=n}^{0} \Post_i}$ to denote  $\Post_n\otimes .. \otimes \Post_0$. By convention ${\displaystyle \bigotimes_{i=-1}^{0} \Post_i}$ is the identity.
-
-\subsection{Weak bisimulation is an equivalence}\label{app-WFH-equiv}
-
-In this section, we first define two alternative definitions, one for weak open transition, one for for weak bisimulation.
-We use these two alternative definitions to show that weak bisimulation is an equivalence, we will also re-use these alternative definitions in the  proofs of the theorems in next sections.
-
-\begin{lemma}[Alternative definition of weak open transitions]
-\label{lem-rel-OT-WOT} Let $A = <J,\mathcal{S}, s_0,V_1,
-    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,V_2,
-    \WT>$ be the
-weak open automata derived from $A$.  The two following statements are equivalent
-%For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
-\begin{enumerate}
-\item Either $   
-\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'$; or \\ 
-there exist   $\set{\beta_{1i}}$, $\set{\beta_{2i}}$, and $\set{\beta_{3i}}$, $\Pred_{1i}$, $\Pred_{3i}$, $\Post_{1i}$, and  $\Pred_2$, $\Post_2$, $n\geq -1$, $m\geq -1$ s.t.\footnote{$n=-1$ (resp.
-$m=-1$) corresponds to the case where there is no $\tau$ transition before (resp.
-after) the transition $\alpha$.}:
-
-\begin{mathpar}
-%\mprset {vskip=.5ex}
-%\inferrule 
-\forall i \in [0..n].\openrule
-    {
-       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
-         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T} \quad \wedge
-\quad
-\openrule
-         {
-           \set{\beta_2},\Pred_2,\Post_2 }
-         {s_2 \OTarrow {\alpha} s'_2} \in \mathcal{T}
-\quad \wedge\\
-\forall i \in [0..m].\openrule
-         {
-           \set{\beta_{3i}},\Pred_{3i},\Post_{3i}    }
-         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}
- \end{mathpar}
-\item  there exist $\set{\gamma}$, $\Pred$, $\Post$ s.t.
- \begin{mathpar}
-%   \Longleftrightarrow  {
-\openrule
-         {
-           \set{\gamma},
-		\Pred, \Post
-				 } {s \OTWeakarrow {\alpha'} s'} \in\WT
-%}
-\end{mathpar}
-where\\
-$
-\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n}^{0}\Post_{1j}}}\\
-s=s_{10} \wedge s_{1(n+1)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
-\displaystyle{
-\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup}\\
-{}~\qquad \displaystyle{\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
-\\
-\Pred=\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=n}^{0}\Post_{1j}}\land\\ 
-{}~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}}\Big)\\
-\Post=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}
-$
-
-\end{enumerate}
-\end{lemma}
-
-\begin{proof} ($\Rightarrow$) We present an induction on $n$ and $m$, focusing on the incrementation on $n$: we prove that the property is valid for $m=-1$, $n=-1$ apply a first induction proof for going from $n$ to $n+1$, a similar induction can be applied to go from $m$ to $m+1$ (omitted).
-\begin{itemize}
-\item The base case there is one transition, so $n=-1$ and $m=-1$, we have:
-\begin{mathpar}
- % \mprset {vskip=.5ex}
-%\inferrule{
- \openrule
-         {
-           \set{\beta},\Pred,\Post}
-         {s \OTarrow {\alpha} s'} \in \mathcal{T}
-%}
-%}
-\end{mathpar} 
-by rule \WTDeux\ we can directly conclude the implication: 
- \begin{mathpar}
- % \mprset {vskip=.5ex}
-%\inferrule{
-% \openrule
-%         {
-%           \set{\beta},\Pred,\Post}
-%         {s \OTarrow {\alpha} s'} \in \mathcal{T}
-%}
-
-\openrule
-         {
-           \set{\beta},\Pred,\Post}
-         {s \OTarrow {\alpha} s'} \in \mathcal{T} \Rightarrow 
-{ \openrule
-         {
-           \vis{\set{\beta}}\!,\Pred,\Post
-				 } {s \OTWeakarrow {\alpha} s'} \in \WT
-}
-\end{mathpar} 
-\item For the inductive step, first we have by induction hypothesis that the formula holds for some lengths $m$ and $n$.
-Induction step is to infer that formula holds for transitions of length  $n+1$.
-We consider the case $n'=n+1$.
-We want to prove (1) $\Rightarrow$ (2) in the lemma, and in (1) we  focus on the case where there is a set of open transitions (this is the case: $s\neq s'$).
-In other words, we consider the sequence of ($n+m+4$) open transitions:
-\begin{mathpar}
-\Big(\forall i \in [0..n+1].\openrule
-    {
-       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
-         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T} \quad \wedge
-\quad
-\openrule
-         {
-           \set{\beta_2},\Pred_2,\Post_2 }
-         {s_2 \OTarrow {\alpha} s'_2} \in \mathcal{T}
-\quad \wedge\\
-~~\qquad\qquad\forall i \in [0..m].\openrule
-         {
-           \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
-         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}
-\Big) 
-\end{mathpar}
-
-By recurrence hypothesis we suppose that  (1) $\Rightarrow$ (2) holds for $n$ and $m$ (compared to the line above, we remove the first $\tau$ transition). We have:\\
-
-$
-%\mprset {vskip=.5ex}
-%\inferrule 
-\Big(\forall i \in [1..n+1].\openrule
-    {
-       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
-         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T} \,\wedge\,
-\openrule
-         {
-           \set{\beta_2},\Pred_2,\Post_2 }
-         {s_2 \OTarrow {\alpha} s'_2} \in \mathcal{T}
-\, \wedge\\
-{}~~\hspace{2.25cm}\forall i \in [0..m].\openrule
-         {
-           \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
-         {s_{3i} \OTarrow {\tau} s_{3(i+1)}}\! \in\! \mathcal{T}
-\Big)  \Rightarrow\!  {
-\openrule
-         {
-           \set{\gamma},
-		\Pred, \Post
-				 } {s'' \OTWeakarrow {\alpha'} s'} \in\WT
-}
-$
-where\\
-\begin{align*}
-s''=s_{10} &\wedge s_{1(n+2)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
-\alpha'=&\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\!\!\Post_{1j}}}\\
-\set{\gamma}=&\mybigdotcup_{i=1}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup\\
-& \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }\\
-\Pred=&\bigwedge_{i=1}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{1}\Post_{1j}}\land\\ 
-&\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}}\Big)\\
-\Post=&\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}
-\end{align*}
-
-We need to prove that   by adding the following open transition the implication remains true:
-\begin{mathpar}
- % \mprset {vskip=.5ex}
-%\inferrule{
- \openrule
-         {
-           \set{\beta_{10}},\Pred_{10},\Post_{10}}
-         {s_{10} \OTarrow {\tau} s_{11}} \in \mathcal{T}%}
-\end{mathpar}
-First by using rule \WTDeux~ we have:
-\begin{mathpar}
-
- \openrule
-         {
-           \set{\beta_{10}},\Pred_{10},\Post_{10}}
-         {s_{10} \OTarrow {\tau} s_{11}} \in \mathcal{T}
-\Rightarrow 
-{ \openrule
-       {
-           \vis{\set{\beta_{10}}}\!,\Pred_{10},\Post_{10}
-				 } {s_{10} \OTWeakarrow {\tau}s_{11}} \in \WT
-}
-\end{mathpar}
-
-On the other hand, by rule \WTUn~ we have the following weak open transition:
-\begin{mathpar}
- \openrule
-         {
-          \emptyset,\True,\Id(s')
-				 } {s' \OTWeakarrow {\tau} s'} \in \WT
-\end{mathpar}
-
-Finally by applying rule \WTTrois~on  the above weak open transitions:
-
-\begin{mathpar}
-  \mprset {vskip=.5ex}
-\inferrule {\openrule
-       {
-           \vis{\set{\beta_{10}}}\!,\Pred_{10},\Post_{10}
-				 } {s_{10} \OTWeakarrow {\tau}s_{11}}\! \in\! \WT
-\quad
-\openrule
-         {
-           \set{\gamma},
-		\Pred, \Post
-				 } {s'' \OTWeakarrow {\alpha'} s'}\! \in\!\WT
-\quad
-\openrule
-         {
-          \emptyset,\True,\Id(s'')
-				 } {s' \OTWeakarrow {\tau} s'}\! \in\! \WT
-\\
-\set{\gamma''}= \vis{\set{\beta_{10}}} \dotcup \set{\gamma}\subst{\Post_{10}}\quad
-\Pred\,''=\Pred_{10}\land\Pred\subst{\Post_{10}}\\%\land (\Pred_3\subst{\Post_2})\subst{\Post_{10}}
-\Post\,''=\Id(s'')\shortotimes\Post\shortotimes\Post_{10} \quad \alpha''=\alpha'\subst{\Post_{10}}
-}
-{
-\openrule
-         {
-          \set{\gamma''}, \Pred\,'',\Post\,''
-				 } 
-         {s_{10} \OTWeakarrow {\alpha''} s'} \in\!\WT
-} \WTTrois
-\end{mathpar}
-where we obtain the conclusion of the lemma, as required with the following assertions (derived from previous assertions):
-\begin{align*}
-s_{10}=s_{10} &\wedge s_{1(n+2)}=s_{2} \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
-\alpha''=&\alpha\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}\subst{\Post_{10}} = \alpha\subst{\bigotimes_{j=n+1}^{0}\Post_{1j}}\\
-\set{\gamma''}=&\mybigdotcup_{i=0}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup\\
-&\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }
-\\
-\Pred=&\bigwedge_{i=0}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{0}\Post_{1j}}\land\\ 
-&\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{0}\Post_{1j}}\Big)
-\\
-\Post=&\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{0}\Post_{1j}
-\end{align*}
-
-The right part of the disjunction, i.e.,
-\begin{mathpar}
-\Big(\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
-\end{mathpar}
-is handled trivially by rule \WTUn. 
-\end{itemize}
-
-\noindent ($\Leftarrow$) We proceed by structural induction on the rules  building  the weak transition (as described in the original definition).
-The recurrence hypothesis being that the  the original definition implies the characterisation (1),with the conditions stated at the bottom of the theorem.
-We consider the different rules:
-
-\begin{itemize}
-\item Case rule \WTUn. We have:
-\begin{mathpar}
-{\openrule
-         {
-           \emptyset,\True,\Id(s)
-				 } {s \OTWeakarrow {\tau} s} \in \WT
-}
-\end{mathpar}
-We can directly conclude by the right part of the disjunction the following:\\
-
-$
-{ \openrule
-         {
-           \emptyset,\True,\Id(s)
-				 } {s \OTWeakarrow {\tau} s} \in\! \WT
-}\! \Rightarrow\! \Big(\alpha = \tau \wedge \set{\gamma}=\emptyset \wedge \Pred \!=\!\True \wedge \Post =\Id(s)\wedge s\!=\!s'\Big)
-$
-\item Case rule \WTDeux. We have:
-\begin{mathpar}
-\openrule
-         {
-           \set{\gamma},\Pred,\Post}
-         {s \OTWeakarrow {\alpha} s'} \in \WT \Rightarrow
-         \openrule
-         {
-           \set{\beta},\Pred,\Post}
-         {s \OTarrow {\alpha} s'} \in \mathcal{T}         
-\end{mathpar}
-where $\set{\gamma} = \vis{\set{\beta}}$.\\
-
-These two cases above prove the implication with $n=-1$ and $m=-1$.
-
-\item Case rule \WTTrois. We have:
-\begin{mathpar}
-  \mprset {vskip=.5ex}
-\inferrule {\openrule
-         {
-           \set{\gamma_1},\Pred_1,\Post_1   }
-         {s \OTWeakarrow {\tau} s'} \in \WT
-\quad
-\openrule
-         {
-           \set{\gamma_2},\Pred_2,\Post_2  }
-         {s' \OTWeakarrow {\alpha} s''} \in \WT
-\quad
-\openrule
-         {
-           \set{\gamma_3},\Pred_3,\Post_3    }
-         {s'' \OTWeakarrow {\tau} s'''} \in\WT
-\\
-\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land \Pred_3\subst{\Post_2\shortotimes\Post_1}
-\\
-\set{\gamma}=\set{\gamma_1}\dotcup \set{\gamma_2}\subst{\Post_1}\dotcup\set{\gamma_3}\subst{\Post_2\shortotimes \Post_1}\\
-\alpha'=\alpha\subst{\Post_1}
-}
-{
-\openrule
-         {
-           \set{\gamma},
-		\Pred,
-				\Post_3\shortotimes{\Post_2}\shortotimes{\Post_1} }
-         {s \OTWeakarrow {\alpha'} s'''} \in\WT
-}
-\end{mathpar}
-
-%where 
-%$\set{\gamma}=\set{\gamma_1} \dotcup \set{\gamma_2} \dotcup \set{\gamma_3}$,
-%$\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}$, and $\Post= ({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K}$
-
-\begin{enumerate}
-
-\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau open transitions such $n_1=n+m+3$, hence by simplification we have (strictly speaking, by induction we might also have the case $\alpha=\tau\land\set \gamma=\emptyset\land \ldots$ but in this case, rule \WTUn~ allows us to obtain a similar reduction with $n_1=1$):
-\begin{mathpar}
-%\inferrule{
-\openrule
-         {
-           \set{\gamma_1},\Pred_1,\Post_1   }
-         {s \OTWeakarrow {\tau} s'} \in\! \WT 
-\Rightarrow \,
- \forall i \in [0..n_1].\openrule
-    {
-       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
-         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T}
-\end{mathpar}
-where \\
-$ 
-s=s_{10} \wedge s_{1{(n_1+1)}}\!=s',\quad
-\displaystyle{\set{\gamma_1}= \mybigdotcup_{i=0}^{n_1} \vis{\set{\beta_{1 i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1 j} } }} \\
-\Pred_1\!=\!\bigwedge_{i=0}^{n_1}(\Pred_{1i} \subst{\bigotimes_{j=i-1}^{0}\Post_{i j}} ), \quad \Post_1= \bigotimes_{i=n_1}^{0} \subst{\Post_{1i}} 
-$
-
-\item Similarly, a series of $m_1$ open transitions such that $m_1=n+m+3$   can be simplified as follows: 
-\begin{mathpar}
-%\inferrule{
-\openrule
-         {
-           \set{\gamma_3},\Pred_3,\Post_3   }
-         {s'' \OTWeakarrow {\tau} s'''} \in\! \WT
-\Rightarrow\, 
-\forall i \in [0..m_1].\openrule
-    {
-       \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
-         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}        
-\end{mathpar}
-where
-\begin{mathpar}
-s''=s_{30}
-
-\land
-
- s_{3{(m_1+1)}}\!=s'''
-
-\land
-
-\displaystyle{\set{\gamma_3}= \mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{3 i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{3 j} } }}
-
-\land
-
-\Pred_3\!=\!\bigwedge_{i=0}^{m_1}(\Pred_{3i} \subst{\bigotimes_{j=i-1}^{0}\Post_{3 j}} )
-
-\land
-
- \Post_3= \bigotimes_{i=m_1}^{0} \subst{\Post_{3i}} 
-\end{mathpar}
-
-\item Concerning the middle reduction, by induction hypothesis there exists a set of open transitions in $\mathcal{T}$ such that:
-\begin{mathpar}
-\openrule
-         {
-           \set{\gamma_2},\Pred_2,\Post_2  }
-         {s' \OTWeakarrow {\alpha'} s''} \in\! \WT
-\Rightarrow 
-\bigg(\forall i \in [0..n_2].\openrule
-    {
-       \set{\beta_{2i}},\Pred_{2i},\Post_{2i}}
-         {s_{2i} \OTarrow {\tau} s_{2(i+1)}} \in \mathcal{T}  \wedge
-
-\openrule
-         {
-           \set{\beta'},\Pred\,',\Post\,' }
-         {s_2 \OTarrow {\alpha''} s_2'} \in \mathcal{T}
- \wedge
-\forall i \in [0..m_2].\openrule
-         {
-           \set{\beta_{2i}'},\Pred_{2i}^{\,\prime},\Post'_{2i}    }
-         {s_{2i}' \OTarrow {\tau} s_{2(i+1)}'} \in \mathcal{T}
-\bigg)         
-\end{mathpar}
-
-where
-\begin{align*}
-s'=s_{20} &\wedge s_{2(n_2+1)}=s_2 \wedge  s_2' = s_{20}' \wedge s_{2(m_2+1)}'=s''\\
-\alpha''=&\alpha'\subst{\bigotimes_{j=n_2}^{0}\Post_{2j}}\\
-\set{\gamma_2}=&\mybigdotcup_{i=0}^{n_2} \vis{\set{\beta_{2i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{2 j} } }  \dotcup  \vis{\set{\beta'}\subst{\bigotimes_{j=n_2}^{0}\Post_{2j}}} \dotcup\\
-&
- \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{2i}} \subst{\bigotimes_{j=i-1}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j=n_2}^{0}\Post_{2j}}}
-\\
-\Pred_2=&\bigwedge_{i=0}^{n_2}\Pred_{2i}\subst{\bigotimes_{j=i-1}^{0}\Post_{2j}}\land\Pred\,' \subst{\bigotimes_{j={n_2}}^{0}\Post_{2j}}\land\\ 
-&\Big(\bigwedge_{i=0}^{m_2}\Pred\,'_{2i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}}\Big)\\
-\Post_2=&\bigotimes_{j=m_2}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}
-\end{align*}
-
-\end{enumerate}
-~~\\
-Therefore, we can deduce that we have:
-\begin{mathpar}
-{ \openrule
-         {
-           \set{\gamma}\!,\Pred,\Post
-				 } {s \OTWeakarrow {\alpha} s'} \in \WT
-}
- \Rightarrow
-\bigg(\forall i\in [0..(n_1\!+\!n_2)].\openrule
-    {
-       \set{\beta_{4i}},\Pred_{4i},\Post_{4i}   }
-         {s_{4i} \OTarrow {\tau} s_{4(i+1)}} \in\mathcal{T} \wedge
-
-\openrule
-         {
-           \set{\beta'},\Pred\,',\Post\,' }
-         {s_2 \OTarrow {\alpha''} s_2'} \in \mathcal{T}
-\wedge\,
-\forall i \in [0..(m_1\!+\!m_2)].\openrule
-         {\set{\beta_{5i}},\Pred_{5 i},\Post_{5i}    }
-         {s_{5i}\OTarrow {\tau} s_{5({i+1})}}\in\mathcal{T}\bigg)  
-\end{mathpar}
-
-such that
-\begin{align*}
-s_{4i}=\begin{cases}
-			s_{1i} & \mbox{if }i<n_1\\
-			s_{2i-n_1} & \mbox{if }i\geq n_1
-	   \end{cases}
-&\qquad\qquad\qquad&
-s_{5i}=\begin{cases}
-			s_{3i} & \mbox{if }i<m_1\\
-s_{2i-m_1}' & \mbox{if }i\geq m_1
-	\end{cases}\\
-\end{align*}
-
- and similarly for $\Pred_{4i}$, $\Pred_{5i}$, $\Post_{4i}$, and $\Post_{5i}$.
-
-Also, we have the following assertions:
-\begin{align*}
-s\!=\!s_{40}& ~\wedge~s_{4(n_1+n_2+1)}\!=s_2 ~\wedge~s_2' = s_{50} ~\wedge~ s_{5(m_1+m_2+1)}\!=\!s'\\
-\alpha''=&\alpha\subst{\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}\\
-\set{\gamma}=&\mybigdotcup_{i=0}^{n_1+n_2} \vis{\set{\beta_{4i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{4 j} } }  \dotcup  \vis{\set{\beta'}\subst{\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}}\dotcup \\
-&\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta_{5i}}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{5i}\shortotimes\Post\,'\shortotimes\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4i}} }\\
-\Pred=&
-\bigwedge_{i=0}^{n_1+n_2}\!\!\Pred_{4i}\subst{\bigotimes_{j=i-1}^{0}\Post_{4j}}\land\Pred\,' \subst{\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\!\Post_{4j}}\land\\ 
-&\quad\bigwedge_{i=0}^{m_1+m_2}\Pred_{5i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{5j}\shortotimes\Post\,'\shortotimes\!\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\!\Post_{4j}}\\
-\Post=&\bigotimes_{j=m_1+m_2}^{0}\!\!\!\Post_{5j}\shortotimes\Post\,'\shortotimes\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\Post_{4j}
-\end{align*}
-
-This concludes the inductive step, showing  that the decomposition expressed by the $\Leftarrow$ direction of the lemma is always possible with the right side conditions. 
-\qedhere
-\end{itemize}
-\end{proof}
-
-\begin{lemma}[Alternative definition of weak bisimulation]\label{lem-alternative-weak-bisim} The definition of weak bisimulation given in Definition \ref{def-Weak-bisim} is equivalent to the following one:
-
- Let $A_1 = <\!J,\mathcal{S}_1, s_0, V_1,
-    \mathcal{T}_1\!>$ and $A_2 = <\!J,\mathcal{S}_2,t_0, V_2, \mathcal{T}_2\!>$ be open automata; $<\!J,\mathcal{S}_1, s_0,V_1,
-    \WT_1\!>$ and $<\!J,\mathcal{S}_2,t_0, V_2, \WT_2\!>$ be the
-weak open automata derived from $A_1$ and $A_2$ respectively.
-For any  states
-$s\in\mathcal{S}_1$ and
-$t\in\mathcal{S}_2$ such that $(s,t|\Pred_{s,t})\in\mathcal{R}$, we 
-   have:
-\begin{itemize}
- \item  For any open transition $\symb{WOT}$ in $\WT_1$:
- \begin{mathpar}
-     \openrule
-         {
-           \gamma_j^{j\in J'},\Pred_{OT},\Post_{OT}}
-         {s \OTWeakarrow {\alpha} s'}
-
-\end{mathpar}
- there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {t \OTWeakarrow {\alpha_x} t_x}
-\end{mathpar}
- such that  $\forall x, J'=J_{x}, (s',t_x|\Pred_{s',x})\in \mathcal{R}$; 
- and  \\
-$\Pred_{s,t} \land \Pred_{OT}\!\implies\!
-\displaystyle{\bigvee_{x\in X}
-   \left( \forall j\in J_x.\gamma_j\!=\!\gamma_{jx}\!\land\! \Pred_{OT_x}
-     \land \alpha\!=\!\alpha_x \!\land\!  
-     \Pred_{s',x}\subst{\Post_{OT}\!\uplus\!\Post_{OT_x}}\right)}$
-
- \item  and symmetrically any open transition from $\symb{WOT}$ in $\WT_2$ can be 
-      covered by a set of weak transitions from $s$ in $\WT_1$.
- \end{itemize}
-
-\end{lemma}
-
-\begin{proof} Note that Definition \ref{def-Weak-bisim} is a particular case of the definition above, thus we only need to prove one direction of the equivalence between the two definitions, namely: \\
-($\Rightarrow$) We prove that Definition \ref{def-Weak-bisim} implies the definition above. In other words,
-suppose that $\Pred_{s,t}\in \mathcal{R}$ 
-%and for any open transition $OT$ in $\mathcal{T}_1$:
-% \begin{mathpar}
-%     \openrule
-%         {
-%           \beta_j^{j\in J},\Pred_{OT},\Post_{OT}}
-%         {s \OTarrow {\alpha} s'}
-%\end{mathpar}
-%there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
-% \begin{mathpar}
-%    \openrule
-%         {
-%           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-%         {t \OTWeakarrow {\alpha_x} t_x}
-%\end{mathpar}
-% such that  $\forall x, J_{x}=\{j\in J|\beta_j\neq\tau\}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
-% and  \\
-% $\Pred_{s,t} \land \Pred_{OT}\\
-% \implies\!\!\!\displaystyle{\bigvee_{x\in X}}
-%   \big(\forall j\in J_x. \vis{\beta_j}=\gamma_{jx}\Rightarrow \Pred_{OT_x}
-%     \land \alpha\!=\!\alpha_x\land  
-%     \Pred_{s',t_x}\subst{\Post_{OT}\shortotimes\Post_{OT_x}}\big)$\\
-and  suppose that the following statement holds:
-\begin{mathpar}
-     \openrule
-         {
-           \gamma_j^{j\in J'},\Pred_{OT},\Post_{OT}}
-         {s \OTWeakarrow {\alpha} s'} \in \WT_1
-
-\end{mathpar}
-Moreover, by using Lemma \ref{lem-rel-OT-WOT} we know that:
-\begin{mathpar}
-    \openrule
-         {
-           \gamma_j^{j\in J'},\Pred_{OT},\Post_{OT}}
-         {s \OTWeakarrow {\alpha} s'} \in \WT_1
-         \Rightarrow
-\bigg(\forall i \in [0..n].\openrule
-    {
-       \beta_{1ij}^{j\in J_1'},\Pred_{1i},\Post_{1i}   }
-         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T}_1  \wedge
-\\{\qquad\qquad\qquad\qquad\qquad}
-\openrule
-         {
-           \beta_{2j}^{j\in J_2'},\Pred_2,\Post_2 }
-         {s_{20} \OTarrow {\alpha'} s_{21}} \in \mathcal{T}_1
- \wedge
-\forall i \in [0..m].\openrule
-         {
-           \beta_{3ij}^{j\in J_3'},\Pred_{3i},  \Post_{3i}  }
-         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}_1
-\bigg)
-\end{mathpar}
-where
-\begin{align*}
-s=s_{10} &\wedge s_{1(n+1)}=s_{20} \wedge s_{21} = s_{30} \wedge s_{3(m+1)}=s'\\
-\alpha=&\alpha'\subst{\bigotimes_{j=n}^{0}\Post_{1j}}\\
-\gamma_j^{j\in J'}=&\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup\\
-&\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }
-\\
-\Pred_{OT}=&\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=n}^{0}\Post_{1j}}\land\\ 
-&\qquad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}}\Big)\\
-\Post_{OT}=&\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}
-\end{align*}
-
-For the sake of simplicity, we prove the rule in the  restricted case where $n$ and $m$ are equal to $0$, hence a single tau open transition will be considered on each side of the potentially visible one.
-The proof may be easily generalized to the multiple tau open transitions by using the same reasoning and \WTTrois~ rule.
-Consider each open transition separately:
-\begin{enumerate}
-\item For the first open transition in $\mathcal{T}_1$:
-\begin{mathpar}
-%\inferrule{
- \openrule
-    {
-       \beta_{1j}^{j\in J_1'},\Pred_1,\Post_1   }
-         {s_{10} \OTarrow {\tau} s_{11}}          
-\end{mathpar}
-by hypothesis we have $(s,t|\Pred_{s,t})\in\mathcal{R}$  and $s=s_{10}$.
-Thus, by  Definition \ref{def-Weak-bisim} we  can deduce there exist weak open transitions $\symb{WOT}_a^{a\in A} \subseteq \WT_2$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j a}^{j\in J_{a}}, \Pred_{OT_a},\Post_{OT_a}}
-         {t \OTWeakarrow {\alpha_{1 a}} u_a}
-\end{mathpar}
- such that  $\forall a, J_{a}=\{j\in J_1'|\beta_{1j}\neq\tau\},   (s_{11},u_a|\Pred_{s_{11},a})\in \mathcal{R}$ and \\
- $\Pred_{s,t} \land \Pred_1\implies\\
- \displaystyle{\bigvee_{a\in A}}
-  \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}\!=\!\gamma_{ja} \!\land\! \Pred_{OT_a}\!
-     \land\! \alpha_{1 a}\!=\!\tau \land  
-     \Pred_{s_{11},a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$
-
- Note that, because $\AlgE\cap\AlgA=\emptyset$  (actions and expressions are disjoint) and $\alpha_{1 a}\!=\!\tau$ we have 
-directly ($\alpha_{1 a}$ cannot be a variable, and cannot contain expressions/variables because $\tau$ has no parameter):
-\begin{mathpar}
-    \openrule
-         {
-           \gamma_{j a}^{j\in J_{a}}, \Pred_{OT_a},\Post_{OT_a}}
-         {t \OTWeakarrow {\tau} u_a}
-\end{mathpar}
-%and\\
-%$\Pred_{s,t} \land \Pred_1\\
-%\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
-%  \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a}
-%     \land    \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$
-%
-
-\item Concerning the middle open transition in $\mathcal{T}_1$:
- \begin{mathpar}
-     \openrule
-         {
-           \beta_{2j}^{j \in J_2'},\Pred_2,\Post_2 }
-         {s_{20} \OTarrow {\alpha'} s_{21}} 
-\end{mathpar}
-we have  $(s_{11},u_a|\Pred_{s_{11},a})\in \mathcal{R}$  and $s_{11}=s_{20}$. Again 
- by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{b}^{b\in B} \subseteq \WT_2$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j b}^{j\in J_{b}}, \Pred_{OT_{b}},\Post_{OT_{b}}}
-         {u_a \OTWeakarrow {\alpha_{2 b}} v_{b}}
-\end{mathpar}
-such that  $\forall b, J_{b}=\{j\in J_2'|\beta_{2j}\neq\tau\}, 
-(s_{21},v_{b}|\Pred_{s_{21},b})\in \mathcal{R}$; \\
- $\Pred_{s_{11},a} \land \Pred_2\implies\\
-\displaystyle{\bigvee_{b\in B}}
- \!\!  \left( \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}\land \Pred_{OT_{b}}\!\land \alpha'\!=\!\alpha_{2 b}\! \land\!  
-     \Pred_{s_{21},b}\subst{\Post_2\uplus\Post_{OT_{b}}}\right)$
-
-\item Similarly to the case 1, we consider the third  open transition in $\mathcal{T}_1$:
-     \begin{mathpar}
-%\inferrule{
- \openrule
-    {
-       \beta_{3j}^{j \in J_3'},\Pred_3,\Post_3   }
-         {s_{30} \OTarrow {\tau} s_{31}} \in \mathcal{T}          
-\end{mathpar}
-From previous case, we have $(s_{21},v_{b}|\Pred_{s_{21},b})\in \mathcal{R}$, and we have $s_{21}=s_{30}$. Then, by
- Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{a}^{c\in C} \subseteq \WT_2$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{jc}^{j\in J_{c}}, \Pred_{OT_{c}},\Post_{OT_{c}}}
-         {v_{b} \OTWeakarrow {\tau} w_{c}}
-\end{mathpar}
- such that  $\forall c, J_{c}= \{j\in J_3'|\beta_{3j}\neq\tau\}, 
-(s_{31},w_{c}|\Pred_{s_{31},c})\in \mathcal{R}$ and \\
- $\Pred_{s_{21},b} \land \Pred_3\implies %\\
-\displaystyle{\bigvee_{c\in C}}
-   \!\left( \forall j\in J_{c}. \vis{\beta_{3j}}\!=\!\gamma_{jc} \! \land\! \Pred_{OT_{c}}\!
-     \land\!  
-     \Pred_{s_{31},c}\subst{\Post_3\uplus\Post_{OT_{c}}}\right)$
-
-\end{enumerate}
-\medskip     
-Based on cases described above by applying \WTTrois~rule on the resulting $\symb{WOT}$s we have:
-
-\begin{mathpar}
-  \mprset {vskip=.5ex}
-\inferrule {
-\openrule
-         {
-           \gamma_{j a}^{j\in J_{a}}, \Pred_{OT_x},\Post_{OT_a}}
-         {t \OTWeakarrow {\tau} u_a}
-\qquad
-\openrule
-         {
-           \gamma_{j b}^{j\in J_{b}}, \Pred_{OT_{ y}},\Post_{OT_{b}}}
-         {u_a \OTWeakarrow {\alpha_2} v_{b}}
-\qquad
-\openrule
-         {
-           \gamma_{jc}^{j\in J_{c}}, \Pred_{OT_{c}}, \Post_{OT_{c}}}
-         {v_{b} \OTWeakarrow {\tau} w_{c}}
-\\ 
-\set{\gamma'}=\gamma_{j a}^{j\in J_{a}} \dotcup \gamma_{jb}^{j\in J_{b}} \subst{\Post_{OT_a}} \dotcup\gamma_{jc}^{j\in J_{c}} \subst{\Post_{OT_{ b}}\shortotimes\Post_{OT_a}}\\
-\Pred=\Pred_{OT_a}\land\Pred_{OT_{b}}\subst{\Post_{OT_a}}\land \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}\\
-\Post= \Post_{OT_{c}} \shortotimes \Post_{OT_{b}}\shortotimes\Post_{OT_{a}}\quad \alpha''=\alpha_{2}\subst{\Post_{OT_a}}\\
-}
-{
-\openrule
-         {
-           \set{\gamma},
-		\Pred, \Post}  
-         {t \OTWeakarrow {\alpha''} w_{c}} 
-} 
- \end{mathpar}
-It remains to be proven that the following statement holds:\\
-$\Pred_{s,t} \land \Pred\implies
- \displaystyle{\bigvee_{x\in X}} 
-  ( \forall j\in J. \gamma_j'=\gamma_{j}  \land \Pred
-     \land \alpha \!=\! \alpha'' \land  
-     \Pred_{s',x}\subst{\Post_{OT}\uplus\Post\,})$\\
-We have:\\
-$\Pred_{OT}= \Pred_1 \wedge \Pred_2\subst{\Post_1} \wedge \Pred_3\subst{\Post_2\shortotimes\Post_1}$\\
-$\Post_{OT}=\Post_3\shortotimes \Post_2\shortotimes\Post_1$\\
-Moreover, we have the following  statement:\\
-$\Pred_{s,t} \land \Pred_1\implies
- \displaystyle{\bigvee_{a\in A}}
- \! \! \left( \forall j\in J_a. \vis{\beta_{1j}}=\gamma_{ja}  \land \Pred_{OT_a}
-      \land  
-     \Pred_{s_{11},a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$\\
-With the conjunction of the predicate $\Pred_2\subst{\Post_1}$ on both sides of the implication, we get:
-\begin{multline*}
-(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies \\
- \bigvee_{a\in A}
-  \!\! ( \forall j\in J_a. \vis{\beta_{1j}}\!=\!\gamma_{ja}\!  \land\! \Pred_{OT_a}\! \land\!
-     \Pred_{s_{11},a}\subst{\Post_1\uplus\Post_{OT_a}}) \wedge \Pred_2\subst{\Post_1\uplus\Post_{OT_a}}  \hspace{-2ex}
-\end{multline*}
-Note that  on the right side of the implication we added  the substitution  of $\Post_{OT_x}$ without affecting the validity of the statement, because  the domain  of the substitution $\Post_{OT_x}$ is disjoint from the others.
-Hence a little rewriting gives:
-\begin{multline*}
-(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies\\
-\bigvee_{a\in A}
-\!\!   \left(\forall j\in J_a. \vis{\beta_{1j}}\!=\!\gamma_{ja}\land \Pred_{OT_a}
-     \!\land(\Pred_{s_{11},a}\wedge\Pred_2)\subst{\Post_1\uplus\Post_{OT_a}} \right)
-\end{multline*}
-
-By replacing the inner predicate $(\Pred_{s_{11},u_a}\wedge\Pred_2)$ by the conclusion of the  statement given in case 2,  the formula becomes: 
-\begin{multline*}(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies\\
-{\bigvee_{a\in A}}
-   \!\!(\forall j\in J_a. \vis{\beta_{1j}}\!\!=\!\gamma_{ja}  \land \Pred_{OT_a}
-      \land ({\bigvee_{b\in B}}(
-    \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}  \land \Pred_{OT_{b}}\!\land 
-    \alpha'\!=\!\alpha_{2 b} \land\\ \Pred_{s_{21},b}\subst{\Post_2\uplus\Post_{OT_{b}}})\subst{\Post_1\uplus\Post_{OT_a}})
-\end{multline*}
-
-This can be rewritten into:
-\begin{multline*}(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1} \implies\\
-{\bigvee_{a\in A}}\, {\bigvee_{b\in B}} 
-(\forall j\in J_a.
-\vis{\beta_{1j}}\!\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-\vis{\beta_{2j}}\!=\!\gamma_{jb}\subst{\Post_1\uplus\Post_{OT_a}}   \land\Pred_{OT_a} \land \\ \Pred_{OT_{b}} \subst{\Post_1\uplus\Post_{OT_a}} \land  (\alpha'\!=\!\alpha_{2 b}) \subst{\Post_1\uplus\Post_{OT_a}} \land \\ \Pred_{s_{21},b}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})
-\end{multline*}
-Since $Post_1$  does not act on $\gamma_{jb}$, nor on $ \Pred_{OT_{b}}$ and $  \alpha_{2}$.
-As well $\Post_{OT_a}$  does not act on $\alpha'$, nor on  $\beta_{2j}$ the formula can be simplified as follows:
-\begin{multline*}(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies\\
-\displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}} 
-(\forall j\in J_a.
-\vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-\vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jb} \subst{\Post_{OT_a}}  \land\Pred_{OT_a} \land \\ \Pred_{OT_{b}} \subst{\Post_{OT_a}} \land \alpha'\subst{\Post_1}=\alpha_{2 b} \subst{\Post_{OT_a}} \land\\ \Pred_{s_{21},b}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})\end{multline*}
-Finally, the conjunction with the term $\Pred_3\subst{\Post_2\shortotimes\Post_1}$ of the both sides of the implication and rewriting, we get:
-\begin{multline*}(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\implies \\
-\displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}} 
-(\forall j\in J_a.\vis{\beta^1_j}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-\vis{\beta_{2j}}\subst{\Post_1}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}\land \Pred_{OT_a}\land\\\Pred_{OT_{b}}\subst{\Post_{OT_a}} \land  \alpha'\subst{\Post_1}= \alpha_{2 b} \subst{\Post_{OT_a}} \land (\Pred_{s_{21},v_b} \land  \Pred_3)\\ \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{b}}\shortotimes\Post_{OT_a}})\end{multline*}
-Again note that because of the domain  of the substitution is independent from some predicates and expressions, we removed $\Post_1$ and  we  added the term $\Post_{OT_{b}}\shortotimes\,\Post_{OT_a}$ in the substitution of the right side of the implication.\\
-Finally, by replacing the predicate $(\Pred_{s_{21},b} \land  \Pred_3)$
-by the conclusion of the  implication given in case 3, we get:
-\begin{multline*}\Pred_{s,t} \land \underbrace{\Pred_1\land \Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}}_{\Pred_{OT}}\implies\\
- {\bigvee_{a\in A}}\, {\bigvee_{b\in B}}\, {\bigvee_{c\in C}} 
-(\forall\! j\in\! J_a.\vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \!\in\! J_{b}.\vis{\beta_{2j}\subst{\Post_{OT_a}}}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}  \land \\
- \forall j\!\in\! J_{c}. \vis{\beta_{3j} \subst{\Post_2\,\shortotimes\,\Post_1}} \!=\!\gamma_{jc} \subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}  \land\\
-   \underbrace{\Pred_{OT_a}\land\Pred_{OT_{b}} \subst{\Post_{OT_a}} \land 
-  \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}}_{\Pred} \land  \underbrace{\alpha'\subst{\Post_1}}_{\alpha}=\underbrace{\alpha_{2 b} \subst{\Post_{OT_a}}}_{\alpha''} \land\\ \Pred_{s_{31},c}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{c}}\shortotimes \Post_{OT_{b}}\shortotimes\Post_{OT_a}}_{\Post}})
-\end{multline*}
-The three for all statements (on $J_a$, $J_b$, and $J_c$) can be concatenated using $\dotcup$, the list union lifted to indexed sets (if $\gamma=\gamma'$ and $\gamma''=\gamma'''$ then $\gamma\dotcup\gamma''=\gamma'\dotcup\gamma'''$).
-\begin{multline*}\forall j\in J_a\uplus J_b\uplus J_c.
-\vis{\beta_{1j}}\dotcup \vis{\beta_{2j}\subst{\Post_{OT_a}}}\dotcup \vis{\beta_{3j} \subst{\Post_2\shortotimes\Post_1}}=\\ ~\hspace{5.5cm} \gamma_{j a} \dotcup \gamma_{jb} \subst{\Post_{OT_a}}  \dotcup \gamma_{jc} \subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}
-\end{multline*}
-We have  $s_{31}=s'$, so can rewrite the formula:\\
-$\Pred_{s,t} \land \Pred_{OT}\implies
-\displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}}\, \displaystyle{\bigvee_{c\in C}} 
-(\forall j\in J.\gamma_j'=\gamma_j \land  \Pred \land \alpha=\alpha''  \land \Pred_{s',c}\subst{\Post_{OT}\uplus\Post\,}$\\
-
-All the combinations of elements in $A$, $B$, and $C$ provides a set $X$ of weak open transitions (each combination of one transition in $A$, one in $B$, and one in $C$ provides one weak open transition in the set $X$, i.e.
-each $x\in X$ corresponds to a triple $(a,b,c)\in A\times B\times C$); this defines a set of weak open transitions indexed over $X$;  each such open transition leads to a $w_c$ that we call $t_x$.
-This re-indexing allows us to conclude:\\
-$\Pred_{s,t} \land \Pred_{OT}\implies
- \displaystyle{\bigvee_{x\in X}} 
-(\forall j\in J.\gamma_j'=\gamma_j \land  \Pred \land \alpha=\alpha''  \land \Pred_{s',x}\subst{\Post_{OT}\uplus\Post\,}$\\
-\end{proof}
-
-%\begin
-\noindent{\bf Theorem~\ref{thm-weak-equiv}}. \emph{Weak FH-Bisimulation is an equivalence}.
- Suppose $\mathcal{R}$ 
-is a weak FH-bisimulation. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
-reflexive, symmetric and transitive.
-%\end{theorem}
-
-With the above lemma, we can use the same technique as for Theorem \ref{thm-equiv}  to prove that a weak FH-bisimulation is an equivalence.
-Indeed, we essentially use the same proof-scheme the main difference concerns  $\beta$ and  $\gamma$.
-Indeed, while the schema of the proof of transitivity was not directly applicable on the definition of weak bisimulation,  Lemma~\ref{lem-alternative-weak-bisim} provides a characterisation of weak bisimulation similar to the definition of strong bisimulation, and thus the same proof scheme is directly applicable.
-
-\subsection{Composition properties}\label{sec:app-composition}
-This section gives decomposition/composition lemmas and their proofs, these are the equivalent of the composition lemmas for open transitions, but applied to weak open automata.
-\begin{lemma}[Weak open transition decomposition]\label{lem-decomposeWOT} 
-	Let $\Leaves(Q)=pLTS_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
-	lemma imply that $Q$ is 
-	not a pLTS but a similar lemma can be proven for a pLTS $Q$}:
-	\[ P[Q]_{j_0}  
-		\models
-		{\openrule
-			{
-				\gamma_j^{j\in J}, \Pred,  
-				\Post}
-			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
-				\ostate{s_i'^{\, i\in L}}}
-		}
-	\]
-		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.  
-		 Then there exist $n$, $\Pred\,'$,  
-		$\Post\,'$,   and for all $p\in[0..n]$ there exist $\beta_p$, $\alpha_p$, $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
-		%\[
-		\begin{mathpar}
-		P\models{\openrule
-			{
-				\gamma_j^{j\in (J_p\setminus \Holes(Q)) \cup \{j_0\}}, 
-				\Pred\,',  
-				\Post\,'}
-			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
-				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
-		}%\]
-\text{\qquad and \qquad}\gamma_{j_0}=[\beta_0..\beta_n]
-	\vspace{-2.2ex}\\\text{and for all $p\in[0..n]$~~}
-		%\[
-		Q\models{\openrule
-			{
-				\gamma_{p j}^{j\in J_p}, \Pred_p,  
-				\Post_p}
-			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
-				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
-		}%\]
-\\
-		\text{such that~\qquad}  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) 
-\text{, }
- \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigotimes_{i=p-1}^{0}\Post_i}, \\
-{~\hspace{2cm}}\Pred \iff \Pred\,'
-		\land \!\!\bigwedge_{p=0}^n(\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i} = \beta_p\land \Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i} ),
-\\
-{~\hspace{2cm}}\Post=\Post\,' \uplus \bigotimes_{p=n}^0
-		\Post_p,   \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\
-		\end{mathpar} 
-where for any $p$, $\Post_p$ only acts upon  variables $\vars(Q)$.
-\end{lemma}
-
-\begin{proof} Suppose that we have: 
-\begin{mathpar}
- P[Q]_{j_0} \models \openrule
-			{
-				{\gamma_j^{j\in J}}, \Pred,  
-				\Post}
-			{\ostate{s_l^{l\in L}} \OTWeakarrow {\alpha}
-				\ostate{s_l'^{\, l\in L}}} 
-\end{mathpar}
-By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
-$ \forall p\! \in [0..m_1]\,		
-	P[Q]_{j_0}\!\models		
-\openrule
-    {
-       \set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
-         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$,  $\qquad  P[Q]_{j_0}	\models \openrule
-         {
-           \set{\beta_2},\Pred_2,\Post_2 }
-         {\ostate{t_l^{l\in L}} \OTarrow {\alpha'} \ostate{{t'}_l^{l\in L}}}
-$ 
-\\
-and 
- $\forall p \in [0..m_2] \,\, P[Q]_{j_0}\!\models \openrule
-         {
-           \set{\beta_{3p}},\Pred_{3p}, \Post_{3p}   }
-         {\ostate{u^{l\in L}_{pl}} \OTarrow {\tau} \ostate{u^{l\in L}_{(p+1)l}}}
-$\\
-where\\
-{\small \begin{align*}
-\forall l\in L.\,&s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l\\
-\alpha=&\alpha'{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}}\\
-\gamma_j^{j\in J}=&\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\! \Post_{1j}}}\dotcup\  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup  
-{\mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }}
-\\
-\Pred=&\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\land
-\bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
-\Post=&\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}
-\end{align*}}
-
-\noindent We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$:
-\begin{enumerate}
-\item For each open transition  $\symb{OT}_p$ in the form ($\set{\beta_{1p}}=\beta_{1pj}^{j\in J_{1p}}$):\\ 
-\[P[Q]_{j_0}\!\models		
-\openrule
-    {
-       {\beta_{1pj}^{j\in J_{1p}}},\Pred_{1p},\Post_{1p}   }
-         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}\] 
-If $Q$ moves then we obtain by Lemma \ref{lem-decompose}:\\
-\begin{small}$P\models{\openrule
-			{
-				(\beta_{1pj})^{j\in (J_{1p}\setminus \Holes(Q)) \cup \{j_0\}}, 
-				{\Pred\,'_{1p}},  
-				{\Post\,'_{1p}}}
-			{\ostate{s_{p l}^{l\in L\setminus L_Q}} \OTarrow {\tau}
-					\ostate{({s_{(p+1) l}})^{l\in L\setminus L_Q}}}
-		}%\]
-	\text{~~and~~} 
-		Q\models{\openrule
-			{
-				(\beta_{1pj})^{j\in J_{1p}\cap\Holes(Q)}, {\Pred\,''_{1p}},  
-				{\Post\,''_{1p}}}
-				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{1p}}
-				\ostate{s_{(p+1)l}^{l\in L_Q}}}
-				}\\%\]\\
-$
-\end{small}
-such that  \\
-$\Pred_{1p} \!\!\iff\!\!
-{\Pred\,'_{1p}}\land {\Pred\,''_{1p}}\land\alpha_{1p}\!=\!\beta_{1pj_0}$, $\Post_{1p}\!=\!{\Post\,'_{1p}}\uplus{\Post\,''_{1p}}$  where ${{\Post\,''_{1p}}}$ is the restriction of $\Post_{1p}$ over   $\vars(Q)$.\\
-Else $Q$ does not move and we have: \\
-\begin{small}
-$P\models{\openrule
-			{
-				(\beta_{1pj})^{j\in (J_{1p}\setminus \Holes(Q)) }, 
-				{\Pred\,'_{1p}},  
-				{\Post\,'_{1p}}}
-			{\ostate{(s_{p l})^{l\in L\setminus L_Q}} \OTarrow {\tau}
-				\ostate{({s}_{(p+1) l})^{l\in L\setminus L_Q}}}
-		}$~~and~~ $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}} $
-\end{small}
-\item Similarly, we have similar open transitions on states $u_{pl}$ (for the final $\tau$ transitions).
-
-\item Finally, for the open transition in the form ($\set{\beta_{2}}=\beta_{2j}^{j\in J_2}$):\\ 
-\[P[Q]_{j_0}	\models \openrule
-         {
-           \beta_{2j}^{j\in J_2},\Pred_2,\Post_2 }
-         {\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'} \ostate{(t'_l)^{l\in L_Q}}}\]
-If $Q$ moves then we  obtain by Lemma \ref{lem-decompose}:\\
-\begin{small}$
-		P\models{\openrule
-			{
-				(\beta_{2j})^{j\in (J_2\setminus \Holes(Q)) \cup \{j_0\}}, 
-				{\Pred\,'_2},  
-				{\Post\,'_2}}
-			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha'}
-				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
-		}%\]
-	\,\text{~~and~~}
-	Q\models{\openrule
-			{
-				(\beta_{2j})^{j\in J_2\cap\Holes(Q)}, {\Pred\,''_2},  
-				{\Post\,''_2}}
-			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_{20}}
-				\ostate{t_l'^{\,l\in L_Q}}}
-		}%\]
-$
-\end{small}\\
-such that  $\Pred_2 \iff {\Pred\,'_2}
-		\land {\Pred\,''_2}\land \alpha_2=\beta_{2j_0}$, $\Post_2={\Post\,'_2}\uplus 
-		{\Post\,''_2}$ where ${\Post\,''_2}$ is the restriction of $\Post_2$ over variables  $\vars(Q)$.
-
-Else $Q$ does not move and we have \\
-$\begin{small} P\models{\openrule
-			{
-				(\beta_{2j})^{j\in (J_2\setminus \Holes(Q)) \cup \{j_0\}}, 
-				{\Pred\,'_2},  
-				{\Post\,'_2}}
-			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha'}
-				\ostate{(t_l)'^{\,l\in L\setminus L_Q}}}
-		}%\]
-	\,\text{~~and~~} \ostate{t_l^{l\in L_Q}} = 
-				\ostate{(t_l')^{\,l\in L_Q}} \end{small}$
-
-\end{enumerate}
-By using  Lemma \ref{lem-rel-OT-WOT}, and denoting $\displaystyle{J=\bigcup_{i=0}^{m_1}J_{1i}\cup J_2\cup \bigcup_{i=0}^{m_2}J_{3i}}$, we can conclude from cases (1), (2) and (3) that we have:
-\begin{mathpar}
-		P\models{\openrule
-			{
-				(\gamma_j')^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
-				\Pred\,',  
-				\Post'}
-			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha''}
-				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
-		}%\]
-\end{mathpar}
-where
-$\alpha''=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}}$\\
-On the other hand, we have:
-$\alpha=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}}\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,''_{1j}}}=\alpha''\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,''_{1j}}}$.\\
-As $\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,''_{1j}}}$ has no effect on variables of $P$ and thus on variables of $\alpha''$, so we have $\alpha=\alpha''$.
-\\
-{\small \begin{align*}
-\forall l\in L.\,&s_l=s_{0l} \wedge s_{(m_1+1)l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)l}=s'_l\\
-{(\gamma_j')}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}=&\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}}} \dotcup\\
-& \mybigdotcup_{i=0}^{m_2}
-\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}} }
-\\
-\Pred\,'=&\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}\land\\ 
-&\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}\\
-\Post'=&\bigotimes_{j=m_2}^{0}\!\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}
-\end{align*}}
-
-Note that for all $j\in J\setminus \Holes(Q)$, $\gamma_j' = \gamma_j$ because for all $l$ $\Post\,'_{1l}$ coincide with $\Post_{1l}$ on the variables of $\beta_{1ij}$, and similarly for $\Post\,'_2$ and $\Post\,'_{3l}$.
-%Concerning $\gamma'_{j_0}$ we have:
-%\[\gamma'_{j_0}=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{{\alpha_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}} \dotcup\\
-%~~\qquad \mybigdotcup_{i=0}^{m_2}
-%\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}} }\]
-
-We introduce the following predicate (we will need it for reasoning on the global predicate and will reason on it along the proof):\\
-$\begin{array}{l}\displaystyle{
-\Pred_\beta=\bigwedge_{p=0}^{m_1}(\beta_{1pj_0}=\alpha_{1p})\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}} \wedge (\beta_{2j_0}=\alpha_{20})\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}} \wedge \\\qquad\qquad
-\displaystyle{
-\bigwedge_{p=0}^{m_2}(\beta_{3pj_0}=\alpha_{3p})
-\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}}
-\end{array}$
-
-Concerning $Q$, we reduce the sequence of OTs to a path for which it moves in all steps.
-In other words, if $Q$ does not move at step $q$, then we have $\ostate{s_{q_l}^{l\in L_Q}} = \ostate{{s}_{(q+1) l}^{l\in L_Q}}$ , then we skip the state $\ostate{{s}_{(q+1) l}^{l\in L_Q}}$, i.e.
-we rename all the following states  $\ostate{s_{p l}^{l\in L_Q}}$ where $p\geq q+1$ into $\ostate{{s}_{(p-1) l}^{l\in L_Q}}$.
-Note that self-loops where $Q$ does an action but stays at the same state are not removed.
-We proceed in the same way  for states named $u$.
-To simplify the proof, we suppose that in case 3, $Q$  moves, else transition 3 of $Q$ should be skipped and the last $s_{p l}$ are equal to the first $u_{0 l}$.
-So we have: \\
-\begin{small}
-$\forall p\! \in\! [0..n_1]~ Q\models{\openrule
-			{
-				(\beta_{1pj}')^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{1p}}},  
-				{{\Post\,''_{1p}}}}
-				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{1p}}
-				\ostate{s_{(p+1)l}^{l\in L_Q}}}
-				}%\]
-,~~$  
-$ Q\models{\openrule
-			{
-				(\beta'_{2 j})^{j\in J\cap\Holes(Q)}, {\Pred\,''_2},  
-				{\Post\,''_2}}
-			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_{20}}
-				\ostate{t_l'^{\,l\in L_Q}}}
-		}%\]
-$
-and \\
-$\forall p \in [0..n_2]~ Q\models{\openrule
-			{
-				(\beta'_{3pj})^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{3p}}},  
-				{{\Post\,''_{3p}}}}
-				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha_{3p}}
-				\ostate{u_{(p+1)l}^{l\in L_Q}}}
-				}%\]
-$
-\end{small}
-\\ 
-such that $n_1 \leq m_1$ and $n_2 \leq m_2$.
-
-By renaming all state names ($s$, $u$ and $t$) with the same state name $v$. We have:
-
-$\forall p \in [0..(n_1\!+\!n_2\!+\!2)]\,\, Q\models{\openrule
-			{
-				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_p}},  
-				{{\Post\,''_p}}}
-				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha'_{p}}
-				\ostate{v_{(p+1)l}^{l\in L_Q}}}
-				}%\]
-$\\ 
-In this equation, and using case 1 above for all $k\in [0\ldots n_1]$ there is a $p\in [0..m_1]$ such that $\alpha_{1p}=\alpha'_k$ (following the re-indexing done in the removal of steps where $Q$ does not move), we know that $\Pred_{1p}$ contains the predicate $( \alpha_{1p}=\beta_{1 p j_0})$.
-Because $\beta_{1 p j_0}$ only contains variables of $P$ and $\alpha'_k$ only variables of $Q$, we have:
-\begin{equation*}
-\begin{split}
-(\alpha_{1p}=\beta_{1pj_0})\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}&\iff
-\alpha_{1p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,''_{1j}}
-= \beta_{1 p j_0}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,'_{1j}} \\
-&\iff\alpha'_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post\,''_{j}}= \beta_{1 p j_0}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,'_{1j}} 
-\end{split}
-\end{equation*}
-We can obtain similar equations for $\alpha'_{n_1+1}$ related with $\beta_{2 j_0}$ and the  $\alpha'_k$ for $k\geq n_1+2$ related with $\beta_{3 p j_0}$ for some $p$.
-Note that the substitutions are however more complex in the other cases.
-Overall we obtain (we skip here the details about the three cases 1, 2, and 3 above that all fall into the same equation because of the re-indexing we perform): 
-\begin{equation}\label{eqproofbeta}
-\Pred_\beta \iff \gamma_{j_0}=
-\vis{[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,''_{j}}|p\in[0..n_1+n_2+2]]}
-\end{equation}
-
-%, 2 and 3 above, we have for all $k\in [0\ldots n_1+n_2+2]$, then there is an action $\beta$ such that $\beta=\beta_{1p j_0}$ s.t.
-$j_0\in J_{1p}$, or $\beta=\beta_{2 j_0}$ with $j_0\in J_{2}$, or $\beta=\beta_{3p j_0}$ s.t.
-$j_0\in J_{3p}$, where $\beta=\alpha_k$, additionally the different $\beta$ are ordered by following the OTs, somehow performing the same re-indexing as  the removal of steps where $Q$ does not move above.
-Overall we have\footnote{under the assumption written above, i.e.
-that $Q$ moves in the middle OT, i.e.
-$j_0\in J_{2}$}:
-%\[ \Pred_* \implies
-%[\beta_{1 p j_0}|j_0\in J_{1p}]\dotcup [\beta_{2 j_0}] \dotcup [\beta_{3 p j_0}|j_0\in J_{3p}] = [\alpha_0..\alpha_{n_1+n_2+2}]
-%\]
-%
-%And thus \[\gamma_{j_0} = []\]
-
-Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha'_p$ some of them may be non-observable (they are $\tau$ transitions).
-By considering the sequence of $\tau$ and non-$\tau$ actions we split the sequence of actions into $n+1$ sub-sequences, such that each subsequence is a sequence of actions containing  only one observable action that will be named $\alpha_p$, and possibly many non-observable ($\tau$) ones.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=6cm]{XFIG/proof-explain}
-\end{center}\caption{Composition of the subsequences}\label{figproof}
-\end{figure}
-
- We can decompose each of the $n+1$ sub-sequences in the following way (see Figure~\ref{figproof}).
-For $k\in [0..n]$ the position of the $k^{\text{th}}$ visible action is  $n_k$.
-For $l\in [1..n]$,  $n'_l$ is any index between $n_{l-1}$ and $n_l$, additionally $n'_0=0$ and $n'_{n+1}=n_1+n_2+3$.
-We obtain $n+1$ sub-sequences  made of the following OTs, for all $k\in [0..n]$ :\\
-\begin{small}
-$\forall p\! \in\! [n'_{k}..(n_k\!-\!1)]~ Q\models{\openrule
-			{
-				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{p}}},  
-				{{\Post\,''_{p}}}}
-				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
-				\ostate{v_{(p+1)l}^{l\in L_Q}}}
-				}%\]
-,\quad
-Q\models{\openrule
-			{
-				\beta_{n_k j}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{n_k}}},  
-				{{\Post\,''_{n_k}}}}
-				{\ostate{v_{n_kl}^{l\in L_Q}} \OTarrow {\alpha'_{{n_k}}}
-				\ostate{v_{(n_k+1)l}^{l\in L_Q}}}
-				}%\]
-$
-\end{small}
-and\\
-\begin{small}
-$\forall p \in [(n_k\!+\!1)..(n'_{k+1}\!-\!1)]\,\, Q\models{\openrule
-			{
-				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{p}}},  
-				{{\Post\,''_{p}}}}
-				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
-				\ostate{v_{(p+1)l}^{l\in L_Q}}}
-				}%\]
-$
-\end{small}
-\\ 
-Thereafter, by Lemma \ref{lem-rel-OT-WOT} we can deduce the following weak open transition:
-\begin{mathpar}
-Q\models{\openrule
-			{
-			(\gamma_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
-				{{\Post_k}}}
-			{\ostate{v_{kl}^{l\in L_Q}} \OTWeakarrow {\alpha_{k}}
-				\ostate{(v_{kl}')^{l\in L_Q}}}
-		}%\]
-\end{mathpar}
-with:
-{\small
-\begin{align*}
-\forall l \in L_Q. &v_{kl}=v_{(n'_{k})l} \wedge v_{kl}'=v_{(n'_k)l}\\
-\alpha_k=&\alpha'_{n_k}{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}}\\
-{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=&{\mybigdotcup_{i=n'_{k}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}} \dotcup\\
-&\mybigdotcup_{i=n_k+1}^{n'_{k+1}-1}
-\vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}} \subst{\bigotimes_{l=i-1}^{n_k\!+\!1}\!\Post\,''_{l}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}} }\\
-\Pred_k=&\bigwedge_{i=n'_{k}}^{n_k\!-\!1}\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\Pred\,''_{n_k} \subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\\ 
-&\bigwedge_{i=n_k+1}^{n'_{k+1}-1}\!\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\!\Post\,''_{j}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{j}}
-\\
-\Post_k= &\bigotimes_{j=n'_{k+1}-1}^{n'_{k}}\!\!\Post\,''_{j}
-\end{align*}
-}
-
-\noindent Note that for all $k\in[0..n-1]$, $v_{kl}'=v_{(k+1)l}$,  $v_{0l}=s_{0l}=s_l$, and $v'_{nl}=v_{(n_1+n_2+3) l}=u_{(n_2+1) l} = s'_l$.
-
-\noindent By definition of $\Post_k$, we have $\displaystyle{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post\,''_{j} = \bigotimes_{j=k-1}^{0}\!\!\Post_{j}}$.
-%In this case, the number of weak open transitions
-%might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.\\
-Consequently,  we have:
-\[\alpha'_{n_k}{\subst{\!\bigotimes_{j=n_k-1}^{0}\!\!\!\Post\,''_{j}}} =
-\alpha'_{n_k}\displaystyle{\subst{\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post''_{j}\otimes\!\!\!\bigotimes_{j=n'_{k}-1}^{0}\!\!\!\Post\,''_{j}}} = \alpha_k\displaystyle{\subst{\!\bigotimes_{j=n'_{k}-1}^{0}\!\!\!\Post\,''_{j}}} =
-\alpha_k\displaystyle{\subst{\!\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}}\]
-\hl{With}~\ref{eqproofbeta}, we now have. Recall that the actions $\alpha_k$ are the actions $\alpha'_{p}$ that are observable: 
-\begin{eqnarray*}
-\Pred_\beta &\iff& \gamma_{j_0}=
-\mybigdotcup_{p=0}^{p=n_1+n_2+2}
-\vis{\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}}\\
-%&\iff&\gamma_{j_0}=
-%\mybigdotcup_{p=0}^{p=n_1+n_2+2}
-%\vis{\alpha_{p}\subst{\bigotimes_{j=p-1}^{n'_p}\!\!\Post_{j}}\subst{\bigotimes_{j=n'_p-1}^{0}\!\!\Post_{j}}}\\
-%\vis{[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n_1+n_2+2]]}\\
-%&\iff& \gamma_{j_0}=
-%\vis{[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[1..n]]}\\
-&\iff& \gamma_{j_0}=
-[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n]]
-\end{eqnarray*}
-
-We need now to show that the set of WOT obtained above verifies the conditions of the lemma, i.e. it is a set of WOT of the form:
-\[	Q\models{\openrule
-			{
-				\gamma_{p j}^{j\in J_p}, \Pred_p,  
-				\Post_p}
-			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
-				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
-		}\]
-with
-\[  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) \qquad\text{trivial}\]
-\[ \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigotimes_{i=p-1}^{0}\Post_i)}\]
-Indeed we have:
-\begin{equation*}
-\begin{split}
-\gamma_j^{j\in J}=&\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!
-\Post_{1j}}}\dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup\\& \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }\\
-\end{split}\end{equation*}
-
-And thus, because $\beta_{pj}^{j\in J\cap \Holes(Q)}$ are equal to the concatenation of  $(\beta'_{1pj})^{j\in J\cap \Holes(Q)}$, $(\beta'_{2j})^{j\in J\cap \Holes(Q)}$, and $(\beta_{3pj}')^{j\in J\cap \Holes(Q)}$ (re-indexed because we skipped some transitions), and additionally $(\beta_{1pj}')^{j\in J\cap \Holes(Q)}$, $(\beta_{2j}')^{j\in J\cap \Holes(Q)}$, and $(\beta_{3pj}')^{j\in J\cap \Holes(Q)}$ are identical to the hole labels $\beta_{1kj}^{j\in J\cap \Holes(Q)}$, $\beta_{2j}^{j\in J\cap \Holes(Q)}$, and $\beta_{3kj}^{j\in J\cap \Holes(Q)}$ (re-indexed) when $Q$ moves\footnote{more precisely, when $Q$ moves either $\beta_{1kj}^{j\in J\cap \Holes(Q)}$ is not empty  and thus $(\beta_{1pj}')^{j\in J\cap \Holes(Q)}=\beta_{1kj}^{j\in J\cap \Holes(Q)}$, or both are empty if the holes of $Q$ perform no action}.
-We can assert a similar equality on post-conditions, i.e.
-between $\Post\,''_p$ and $\Post\,''_{1k}$, $\Post\,''_{2}$, $\Post\,''_{3k}$ where $\Post\,''_{1p}$ is the restriction of $\Post_{1p}$ over $\vars(Q)$ (see initial decomposition, case 1, 2, and 3 above).
-Overall, we have
-$\forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i$ (see above):\\
-{\scriptsize \begin{equation*}
-\begin{split}
-\gamma_j^{j\in J\cap \Holes(Q)}&=\mybigdotcup_{i=0}^{m_1} \vis{\set{(\beta_{1i}')}\subst{\bigotimes_{j=i-1}^{0}\!\!
-\Post''_{1j}}}\dotcup  \vis{\set{\beta'_2}\subst{\bigotimes_{j=m_1}^{0}\Post''_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}} }\\
-&=\mybigdotcup_{k=0}^n \left( \mybigdotcup_{i=n'_k}^{n'_{k+1}-1}\vis{\beta_{ij}^{j\in J\cap \Holes(Q)}\subst{\bigotimes_{j=i-1}^{n'_k}\!\!\Post''_{j}\bigotimes_{j=n'_k-1}^{0}\!\!\Post''_{j}}}\right)\\
-&=\mybigdotcup_{k=0}^n \left( \gamma_{kj}^{j\in J\cap \Holes(Q)}\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{k}}\right)
-\end{split}\end{equation*}
-}
-Next, we have
-\[\Pred = \displaystyle{\Pred\,'
-		\land \!\!\bigwedge_{p=0}^n\Big((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i}) = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i}) \Big)}\]
-Indeed,
-\begin{scriptsize}
-\begin{align*}
-\Pred&\iff\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\land
-\bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
-&\iff\bigwedge_{i=0}^{m_1}\left(\Pred\,'_{1i}
-		\land {\Pred\,''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}\right)\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}} \\
-&\qquad\land\left(\Pred\,'_{2}
-		\land {\Pred\,''_{2}}\land \alpha_{20}=\beta_{2j_0}\right)\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
-&\qquad\land\bigwedge_{i=0}^{m_2} \left(\Pred\,'_{3i}
-		\land {\Pred\,''_{3i}}\land \alpha_{3i}=\beta_{3ij_0}\right) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\displaybreak[0]\\
-&\iff\bigwedge_{i=0}^{m_1}\left((\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{1j}})
-		\land ({\Pred\,''_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,''_{1j}})\land (\alpha_{1i}=\beta_{1ij_0})\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\right) \\
-&\qquad\land \left(\Pred\,'_{2}\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}
-		\land {\Pred\,''_{2}} \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \land (\alpha_{20}=\beta_{2j_0})\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \right) \\
-&\qquad\land\bigwedge_{i=0}^{m_2} \Bigg(\Pred\,'_{3i} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} 
-		\land {\Pred\,''_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}  \\
-		 & \qquad \land (\alpha_{3i}=\beta_{3ij_0}) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\Bigg)  \\
-&\iff \Pred\,'\land\bigwedge_{k=0}^n\Pred_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}\land\Pred_\beta
-\\&\iff \Pred\,'\land\bigwedge_{k=0}^n\Pred_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}\land
-(\gamma_{j_0}=[\alpha_{i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{j}}|i\in[0..n]])
-\end{align*}
-\end{scriptsize}
-which is exactly what is needed with $\gamma_{j_0}=[\beta_0..\beta_n]$.
-
-Finally we have~~
-$\Post=\displaystyle{\Post\,' \uplus \bigotimes_{p=n}^0
-		\Post_p}$\quad
-because
-{\small \begin{align*}
-\Post&=\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}\\
-&=\bigotimes_{j=m_2}^{0}\!\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j} \uplus \bigotimes_{j=m_2}^{0}\!\!\Post\,''_{3j}\shortotimes\Post\,''_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,''_{1j}\\
-&=\Post\,' \uplus \bigotimes_{j=n'_{n+1}-1}^{0}\!\!\Post\,''_{j}
-\end{align*}}
-Which concludes because we have we have $\displaystyle{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post\,''_{j} = \bigotimes_{j=k-1}^{0}\!\!\Post_{j}}$.
-%
-%Consequently, we have $n$ weak open transitions  $\symb{WOT}_k$ such that $k\in [1..n]$.
-%Therefore, we can conclude that we have for all $k\in [1..n]$:  
-%\begin{mathpar}
-%Q\models{\openrule
-%			{
-%			\gamma_{kj}^{j\in J_k}, {\Pred_k}, {\Post_k}}
-%			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
-%				\ostate{s_{(p+1)l}^{l\in L_Q}}}
-%		}%\]
-%\end{mathpar}
-%
-%%By considering $n=m_1+m_2+2$,  and $\forall p \in [0..n]$: \\
-%%$\Pred_{p}= \left\{
-%% \begin{array}{ll}
-%%\Pred_{1p} & \mbox{if }p<m_1\\
-%%\Pred_{2} & \mbox{if } p=m_1\\
-%%\Pred_{1(p-m_1)} & \mbox{if }p\geq m_1\\
-%%\end{array}
-%%\right. 
-%%\quad$
-%% $\qquad
-%%\Post_{p}= \left\{
-%% \begin{array}{ll}
-%%\Post_{1p} & \mbox{if }p<m_1\\
-%%\Post_{2} & \mbox{if } p=m_1\\
-%%\Post_{1(p-m_1)} & \mbox{if }p\geq m_1\\
-%%\end{array}
-%%\right. 
-%%$\\
-%%and similarly for $\beta_p$. Thus, we can rewrite $\gamma$ given in the hypothesis as: \\
-%%$\set{\gamma}= \displaystyle{\mybigdotcup_{p=0}^{n}
-%%\vis{\set{\beta_{p}}}\subst{\bigotimes_{p=n}^{0} \Post_{p}}}$\\
-%Furthermore, still by hypothesis we have:\\
-%$\Pred=\displaystyle{\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }\land \\
-%~\qquad \quad \bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}$\\
-%By replacing $\Pred_{1i}$,  $\Pred_2$, and $\Pred_{3i}$ by their equivalent formula obtained from cases 1, 2 and 3 we have:\\
-%$\Pred =\displaystyle{\bigwedge_{i=0}^{m_1}({\Pred'_{1i}}
-%		\land {\Pred''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}) \bigotimes_{j=i-1}^{0}\subst{\Post_{1j}}\land}\\
-%~~\qquad\qquad({\Pred'_2}\land {\Pred''_2}\land \alpha_2=\beta_{2j_0})	\bigotimes_{i=m_1}^{0}\subst{\Post_{1i}}\land\\
-%~~\qquad\qquad\bigwedge_{i=0}^{m_2} ({\Pred'_{3i}}\land {\Pred''_{3i}}\land \alpha_{3i}=\beta_{3ij_0})
-%\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}$\\
-%By distribution of the substitution operation over the logical operator we reformulate as:\\
-%$\Pred= \displaystyle{\big(\bigwedge_{i=0}^{m_1}
-%{\Pred'_{1i}}\bigotimes_{j=i-1}^{0}\subst{{\Post'_{1j}}}\big)
-%\land{\Pred'_2}\bigotimes_{i=m_1}^{0}\subst{{\Post'_{1i}}}\land} \\
-%~~\qquad\qquad\bigwedge_{i=0}^{m_2}{\Pred'_{3i}}\bigotimes_{j=i-1}^{0}\subst{{\Post'_{3j}}}\subst{{\Post'_2}}\bigotimes_{j=m_1}^{0}\subst{{\Post'_{1j}}} \land\\	
-%~\qquad\qquad\bigwedge_{i=0}^{m_1}({\Pred''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}) \bigotimes_{j=i-1}^{0}\subst{\Post_{1j}}\land({\Pred''_2}\land \alpha_2=\beta_{2j_0})	\bigotimes_{i=m_1}^{0}\subst{\Post_{1i}}\land\\
-%~\qquad\qquad\bigwedge_{i=0}^{m_2} ({\Pred''_{3i}}\land \alpha_{3i}=\beta_{3ij_0})\bigotimes_{j=i-1}^{0}\subst{\Post_{3j}}\subst{\Post_2}  \bigotimes_{i=m_1}^{0}\subst{\Post_{1i}}
-%$\\		
-%Thus, we can write the formula as follows:\\
-%$\Pred= \Pred\,' \wedge \displaystyle{\bigwedge_{p=0}^{n}}((\alpha_p= \beta_{pj_0}\land \Pred_p)\bigotimes_{i=p-1}^{0}\Post_i)$\\
-%We proceed the same way with the postcondition,  we have:\\
-%$\Post=\displaystyle{\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}$\\
-%By replacing ${\Post_{1i}}$,  $\Post_2$, and ${\Post_{3i}}$ their values obtained from the cases 1, 2, and 3, and because the ${\Post'_i}$ and ${\Post''_i}$ are independent (the ${\Post'_i}$ concern the leaves of $P$ while the ${\Post''_i}$ concern the leaves of $Q$), we obtain:\\
-%$\Post= \displaystyle{\bigotimes_{i=m_2}^{0}\subst{{\Post'_{3i}}\uplus 
-%		{\Post''_{3i}}} \subst{{\Post'_2}\uplus 
-%		{\Post''_2}} \bigotimes_{j=m_1}^{0}\subst{ {\Post'_{1i}}\uplus 
-%		{\Post''_{1i}}}}\\
-%~~\qquad= \bigotimes_{i=m_2}^{0}{\Post'_{3i}}\subst{{\Post'_2}}\bigotimes_{j=m_1}^{0}\subst{{\Post'_{1j}}} \uplus \bigotimes_{i=m_2}^{0}{\Post''_{3i}}\subst{{\Post''_2}}\bigotimes_{j=m_1}^{0}\subst{{\Post''_{1j}}} \\
-%~~\qquad= \Post' \uplus \bigotimes_{j=n}^{0} \Post_j $\\
-%\qed
-\end{proof}
-
-\begin{lemma}[Weak open transition composition]\label{lem-Weakcompose1} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
-	Suppose $j_0\in J$  and:\\[-1ex]
-\begin{mathpar}
-%\[
-P\models{\openrule
-	{
-		\beta_j^{j\in J}, 
-		\Pred,  
-		\Post}
-	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
-		\ostate{(s_i')^{\, i\in L}}}
-}
-\quad\text{~~and~~}\quad
-Q\models{\openrule
-	{
-		\set{\gamma},
-		 \Pred_Q,  
-		\Post_Q}
-	{\ostate{s_{i}^{i\in L_Q}} \OTWeakarrow {\alpha_Q}
-		\ostate{(s'_{i})^{\, i\in L_Q}}}
-}%\]
-\end{mathpar}
-
-Let 
-%J_Q=\displaystyle{\bigcup_{t=0}^nJ_{t}}
-\qquad
-$\Pred\,'=\Pred\land (\beta_{j_0}=\alpha_Q\land \Pred_Q) \quad\text{~~and~~}\quad
-%\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
-\Post\,'=\Post\uplus\Post_Q
-$
-
-Then, we have
-{\small	\[ P[Q]_{j_0}  
-	\models
-	{\openrule
-		{
-			\set{\gamma}\uplus\vis{\beta_j^{j\in J\setminus \{j_0\}}}, 
-			\Pred\,',  \Post\,'
-			 }
-		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
-			\ostate{(s_i')^{\, i\in L\uplus L_Q}}}
-	}
-	\]}
-\end{lemma}
-\begin{proof}
-By  Lemma \ref{lem-rel-OT-WOT} we can decompose the WOT of $Q$ into  a series of $k+1$ and $k'+1$ tau open transitions and an $\alpha'_Q$ open transition (observable or not depending on $\alpha_Q$):
-\begin{mathpar}
-\forall h\!\in\![0..k].Q\models\openrule
-    {\set{\beta_{1h}},\Pred_{1h},\Post_{1h}   }
-         {\ostate{{(s_{1h})}} \OTarrow {\tau} \ostate{{(s_{1(h+1)})}}}, \quad
-Q\models{\openrule
-	{
-		\set{\beta_2},
-		 \Pred_2,  
-		\Post_2}
-	{\ostate{s_{20}}\OTarrow {\alpha'_Q}
-		\ostate{s_{21}}}
-}, \\ \quad\text{~~and~~}\quad 
-\forall h \in [0..k'].Q\models\openrule
-         {
-           \set{\beta_{3h}},\Pred_{3h}, \Post_{3h}}
-         { \ostate{(s_{3h})} \OTarrow {\tau} \ostate{(s_{3(h+1)})}}
-\end{mathpar}
-such that\\
-
-\begin{small}
-$s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$
-\begin{align*}
-\alpha_Q=&\alpha'_Q\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}\\
-\set{\gamma}=&\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{j=h-1}^{0}\!\! \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=k}^{0}\Post_{1j}}} \dotcup%\\
-		%&
- \mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{j=h-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=k}^{0}\Post_{1j}} }\\
-\Pred_Q=&\bigwedge_{h=0}^{k}\!\Pred_{1h}\subst{\!\bigotimes_{j=h-1}^{0}\!\!\!\Post_{1 j}}\land \Pred_2\subst{\bigotimes_{h=k}^{0}\!\Post_{1h}}\land%\\
-%&
-	\!\bigwedge_{h=0}^{k'}\!\Pred_{3h}\subst{\!\! 	\bigotimes_{j=h-1}^{0}\!\!\!{\Post_{3j}}\otimes{\Post_2}  \otimes\bigotimes_{h=k}^{0}\!\!\Post_{1h}}\\
-\Post_Q=&\bigotimes_{h=k'}^{0}\!\!\Post_{3h}\otimes\Post_2\otimes\bigotimes_{j=k}^{0}\!\!\Post_{1j}
-\end{align*}
-
-\end{small}
-\begin{enumerate}
-
-\item For the first $k$ open tau transitions, by Definition \ref{def:Non-ObsTau} $P$ can necessarily make a tau open transition if the hole indexed $j_0$ makes a tau action.
-So by Lemma \ref{lem-compose} we obtain $k$ open transitions in the form:
-\[P[Q]_{j_0}\!\models		
-\openrule
-    {
-       \set{\beta_{1h}},{\Pred_{1h}},{\Post_{1h}}   }
-         {\ostate{s_{1h}\uplus s^{i\in L}_{i} } \OTarrow {\tau} \ostate{s_{1(h+1)}\uplus s^{i\in L}_{i}}}\]
-
-\item For the possibly observable open transition.  By Lemma \ref{lem-compose} with the lemma hypotheses we obtain:\\ 
-	\[ P[Q]_{j_0}  
-	\models
-	{\openrule
-		{
-			{\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}, 
-			\Pred\land\Pred_2\land \alpha_Q=\beta_{j_0 },  
-			\Post\uplus \Post_2}
-{\ostate{s^{i\in L}_{i}\uplus s_{20}} \OTarrow {\alpha} \ostate{{s'}^{i\in L}_{i}\uplus s_{21}}}
-	}
-	\]
-
-%
-%\[P[Q]_{j_0}\!\models		
-%\openrule
-%    {
-%       {\beta^i_{p j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2},{\Pred_p}\!\!'',{\Post_p}\!\!''   }
-%         {\ostate{s^{i\in L \uplus L_Q}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L\uplus L_Q }_{(p+1)i}}}\] \\
-% such that  ${\Pred_p}\!\!'' \iff {\Pred_p}
-%		\land {\Pred_p}\!\!'\land \alpha_t=\beta_{j_0}$, ${\Post_p}\!\!''={\Post_p}\uplus 
-%		{\Post_p}\!\!'$\\ 
-\item We proceed in the same way as the first item for $k'$ last weak open transitions, and we obtain $k'$ open tau transitions.
-\end{enumerate}
-
-Using Lemma \ref{lem-rel-OT-WOT}, from cases $(1)$, $(2)$ and $(3)$ we get: 
-\[P[Q]_{j_0}\!\models		
-\openrule
-    {
-\set{\gamma_c}, \Pred_c,
-\Post_c}
-         {\ostate{s_{10}\uplus s^{i\in L}_{i}} \OTWeakarrow {\alpha'} 
-	\ostate{{{s'}^{i\in L}_{i}\uplus s_{3(k'+1)}}}}\] 
-where ~~
-$\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$
-and $\alpha=\alpha'$  because $\Post_{1j}$ acts on variables of $Q$ and $\alpha$ contains only variables of $P$.
-\begin{small}
-\begin{align*}
-\set{\gamma_c}=&\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{i=h-1}^{0}\!\!
-\Post_{1i} } }  \dotcup  \vis{({\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2})\subst{\bigotimes_{i=k}^{0}\Post_{1i}}} \dotcup\\
-&\mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{i=h-1}^{0}\!\!\Post_{3i}\shortotimes\Post_2\shortotimes\bigotimes_{i=k}^{0}\Post_{1i}} }\\
-=&\set{\gamma}\uplus\vis{\beta_j^{\in J\setminus \{j_0\}}} \quad  \text{ because $\Post_{1j}$  does not act on variables of $\beta_j$.}  
-\displaybreak[0]\\
-\Pred_c=&
-\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_{1i}}\land
-\left(Pred\land\Pred_2\land \alpha'_Q=\beta_{j_0}\right) \subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land\\
-&\bigwedge_{h=0}^{k'}{\Pred_{3h}}\subst{\bigotimes_{i=h-1}^{0}{\Post_{3i}}\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}
-\\
-\Post_c=&(\bigotimes_{i=k'}^{0}{\Post_{3i}})\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}
-\end{align*}
-\end{small}
-\noindent Note that we have $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$.
-
-Note also that $\Post$ only acts on variables of $P$ while $\Post_{1i}$ only acts on  variables of $Q$.
-We conclude on predicate and posts as follows\footnote{$\Post_{1i}$ only has an effect on variables of $Q$ and thus does not modify $\Pred$ or $\beta_{j_0}$}:
-\begin{equation*}
-\begin{split}
-\Pred_c&=\Pred_Q\land\Pred\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land
-(\alpha'_Q=\beta_{j_0})\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\\
-&=\Pred_Q\land\Pred\land \alpha_Q=\beta_{j_0}\\[.3ex]
-\Post_c&=\Post\uplus\Post_Q \qedhere
-\end{split}
-\end{equation*}
-\end{proof}
-\smallskip
-\begin{lemma}[Weak open transition composition]\label{lem-Weakcompose} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
-Suppose $j_0\in J$ and $\gamma_{j_0}=[\beta_0..\beta_n]$ and additionally:\\[-2ex]
-\begin{mathpar}
-%\[
-P\models{\openrule
-	{
-		\gamma_j^{j\in J}, 
-		\Pred,  
-		\Post}
-	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
-		\ostate{s_i'^{\, i\in L}}}
-}
-\qquad\text{~~and for all $p\in[0..n]$~~}\quad
-Q\models{\openrule
-	{
-		\gamma_{pj}^{j\in J_p},
-		 \Pred_p,  
-		\Post_p}
-	{\ostate{s_{pi}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
-		\ostate{s_{(p+1) i}^{\, i\in L_Q}}}
-}%\]
-\end{mathpar}
-
-Let 
-\begin{mathpar}
-J_Q=\displaystyle{\bigcup_{p=0}^nJ_{p}}
-
-\forall{i\in L_Q}.\,s_i=s_{0i}~~\land~~s'_i=s_{(n+1) i}
-
-\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}\subst{\bigotimes_{k=p}^{0}{\Post_k}}}
-
-\Pred\,'=\Pred\land \bigwedge_{p=0}^{n}(\alpha_p=\beta_p\land \Pred_p)\subst{\bigotimes_{i=p-1}^{0}\Post_i}
-
-\Post\,'=\Post\uplus\bigotimes_{p=n}^{0}
-		\Post_p
-\end{mathpar}
-Then, we have
-	\[ P[Q]_{j_0}  
-	\models
-	{\openrule
-		{
-			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
-			\Pred\,',  \Post\,'
-			 }
-		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
-			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
-	}
-	\]
-\end{lemma}
-
-\begin{proof} Suppose we have:
-\begin{mathpar}
-%\[
-P\models{\openrule
-	{
-		\gamma_j^{j\in J}, 
-		\Pred,  
-		\Post}
-	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
-		\ostate{s_i'^{\, i\in L}}}
-}
-\end{mathpar}
-By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
-%\begin{mathpar}
-\begin{small}
-$\forall p\!\in\![0\,..\,m_1].P\models\openrule
-    {{\beta_{1pj}^{j\in J_{1p}}},\Pred_{1p},\Post_{1p}   }
-         {\ostate{{(s_{1pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s_{1(p+1)i})}^{i\in L}}},  \quad
-P\models\openrule
-         {\beta_{2j}^{j\in J_2},\Pred_2,\Post_2 }
-         {\ostate{({s_{20i}})^{i\in L}} \OTarrow {\alpha'} \ostate{({s_{21i}})^{i\in L}}} $ 
-\\
-and  $\forall p \in [0\,..\,m_2].P\models\openrule
-         {
-           \beta_{3pj}^{j\in J_{3p}},\Pred_{3p}, \Post_{3p}}
-         { \ostate{(s_{3pi})^{i\in L}} \OTarrow {\tau} \ostate{(s_{3(p+1)i})^{i\in L}}}$
-\end{small}
-%\end{mathpar}
-
- where:
-{\small
-\begin{align*}
-\forall i\in L.&~~s_i=s_{10 i} \wedge s_{1(m_1+1) i}=s_{20i} \wedge  s_{21i}= s_{30 i} \wedge s_{3(m_2+1) i}=s'_i\\
-\alpha=&\alpha'{\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \\
-\gamma_j^{j\in J}=&{\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigotimes_{k=i-1}^{0}\!\!
-\Post_{1k} } }  \dotcup \, \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}}\, \dotcup\\
-&\mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{3p}} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}\\
-\Pred=&{\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\subst{\!\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}\big)\land\Pred_2\subst{\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\land}%\\ 
-%&
-{\bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\bigotimes_{j=p-1}^{0}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}}\\
-\Post=&{\bigotimes_{p=m_2}^{0}\Post_{3p}\otimes\Post_2\otimes\bigotimes_{j=m_1}^{0}\Post_{1j}}
-\end{align*}
-}
-
-Note that, for $l\in\{1,3\}$ if $\beta_{l p j_0}=\tau$, then, because of Definition \ref{def:Non-ObsTau}, $P$ necessarily makes a $\tau$ open transition and remains in the same state, e.g.
-$s_{1pi} = s_{1(p+1)i}$.
-Thus without loss of generality, we can bypass such an open transition and obtain another decomposition of the WOT without the open transition that requires ${\beta_{lp{j_0}}}=\tau$.
-We can thus  suppose that for all $p$ and $l$ we have ${\beta_{lp{j_0}}}\neq\tau$ or $j_0\not\in J_{1 p}$.
-To avoid a special case, we suppose that the hole $j_0$ moves during the OT $\alpha'$, i.e.
-$\beta_{2 j_0}=\beta_{m}$ for some $m$.
-Additionally, $\beta_{m}\neq \tau$, else we would have $\alpha=\alpha'=\tau$ and the $\alpha'$ OT could be also removed from the reduction, leading to a particular and simpler case.
-
-We introduce $n_i^{i\in[0..m-1]}$, and $(n'_i)^{i\in[m+1..n]}$ the indices of the steps in 
-which the hole $j_0$ moves in the 3 sets of OTs above ($\beta_m$ is the action that matches the hole $j_0$ in the OT $\alpha'$), in other words, we have for all $i$, $\beta_{1 n_i j_0}$ a visible action, as additionally:\\
-{\small
-\begin{align*}
-\gamma_{j_0}=&~[\beta_0..\beta_n]\\
- =&\!\!
-{\mybigdotcup_{\substack{i=0\\j_0\in J_{1i}}}^{m_1}\!\!\!
-\vis{{\beta_{1ij_0}}\subst{\!\bigotimes_{k=i-1}^{0} \!\!\!\Post_{1k} } }  \,\dotcup\, \vis{{\beta_{2j_0}}\subst{\!\bigotimes_{k=m_1}^{0}\!\!\Post_{1k}}}}\dotcup %\\
-%&
-{ \!\mybigdotcup_{\substack{i=0\\j_0\in J_{3i}}}^{m_2}\!\! \vis{{\beta_{3ij_0}} \subst{\!\bigotimes_{k=i-1}^{0}\!\!\!\Post_{3k}\shortotimes\Post_2\shortotimes
-\!\bigotimes_{k=m_1}^{0}\!\!\Post_{1k}}}}
-\end{align*}}
-
-\noindent We have, by definition of $n_i$ and $n'_i$:\\
-$\displaystyle{\forall{i\in[0\,..\,m\!-\!1]}, \beta_{1 n_i j_0}\subst{\bigotimes_{k=n_i-1}^{0}\Post_{1k}}=\beta_i}$, \qquad$\displaystyle{\beta_{2 j_0}\subst{\bigotimes_{k=m_1}^{0} \Post_{1k} }=\beta_m}$, and \\
-$\displaystyle{\forall{i\in[m\!+\!1\,..\,n]}, \beta_{3 n_i' j_0}\subst{\bigotimes_{k=n_i'-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}=\beta_i}$\\
-
-\noindent Now, we compose OTs for each of the case above (depending on the OT of $P$):
-\begin{enumerate}
-\item For the first $\tau$ OTs, i.e, $p\in [0\,..\,m_1]$. We have: \\
-Either there is $i$ such that $p=n_i$, and thus $\beta_i$ and $\beta_{1 p j_0}$ are defined. In this case by Lemma~\ref{lem-Weakcompose1},  we have: 
-\[ P[Q]_{j_0}  
-	\models
-	{\openrule
-		{
-			\set{\gamma'_{1p}}, 
-			\Pred\,'_{1p},  \Post\,'_{1p}
-			 }
-		{\ostate{s_{1pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTWeakarrow {\tau}
-			\ostate{s_{1(p+1)j}^{\, j\in L}\uplus s_{(i+1)j}^{j\in L_Q} } }
-	}
-	\]
-with 
-\begin{mathpar}
- \set{\gamma'_{1p}}=\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{1pj}^{j\in J_{1p}\setminus \{j_0\}}}
-
-\Pred\,'_{1p}=\Pred_{1p}\land (\beta_{1pj_0}=\alpha_i\land \Pred_i)
-
- \Post\,'_{1p}=\Post_{1p}\uplus\Post_i
-\end{mathpar}
-
-Or $j_0\not \in \dom(\beta_{1 p})$ and $Q$ does not move in the composed reduction. In this case there is no $i$ such that $p=n_i$, but there is $i$ such that $p\in]n_i .. n_{i+1}[$, and
-\[P[Q]_{j_0} \models\openrule
-    {\set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
-         {\ostate{s_{1pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTarrow {\tau} \ostate{s_{1(p+1)j}^{j\in L}\uplus s_{ij}^{j\in L_Q}}}
-\]
-and thus we also have a weak OT by Definition \ref{def:buildweakOT} (rule (\WTDeux)):
-\[P[Q]_{j_0} \models\openrule
-    {\set{\gamma'_{1p}},\Pred\,'_{1p},\Post\,'_{1p}   }
-         {\ostate{s_{1pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTWeakarrow {\tau} \ostate{s_{1(p+1)j}^{j\in L}\uplus s_{ij}^{j\in L_Q}}}
-\]
-with 
-$\set{\gamma'_{1p}}=\set{\vis{\beta_{1p}}}, \Pred\,'_{1p}=\Pred_{1p}, \Post\,'_{1p}=\Post_{1p}$\\
-
-\item Similarly, for the middle OT with label $\alpha$:
-\[P[Q]_{j_0}\models\openrule
-         {	\set{\gamma'_2},\Pred\,'_2,\Post\,'_2 }
-         {\ostate{{(s_{20j})}^{j\in L}\uplus (s_{mj})^{j\in L_Q}}\OTWeakarrow {\alpha'} \ostate{{(s_{21j})}^{j\in L}\uplus (s_{(m+1)j})^{j\in L_Q}}}\]
-with
-\begin{mathpar}
-\set{\gamma'_2}=\gamma_{m j}^{j\in J_m}\uplus\vis{\beta_{2j}^{j\in J_2\setminus \{j_0\}}}
-
-\Pred\,'_{2}=\Pred_{2}\land (\beta_{2j_0}=\alpha_m\land \Pred_m)
-
-\Post\,'_{2}=\Post_{2}\uplus\Post_m
-\end{mathpar}
-
-\item For the last $\tau$ OTs, i.e, $p\in [0\,..\,m_2]$. We have similarly to the first case:\\
- Either there is $i$ such that $p=n'_i$, and thus $\beta_i$ and $\beta_{1 p j_0}$ are defined. In this case by Lemma~\ref{lem-Weakcompose1}, we have: 
-	\[ P[Q]_{j_0}  
-	\models
-	{\openrule
-		{
-			\set{\gamma'_{3p}}, 
-			\Pred\,'_{3p} ,  \Post\,'_{3p} 
-			 }
-		{\ostate{s_{3pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTWeakarrow {\tau}
-			\ostate{s_{3(p+1)j}^{\, j\in L}\uplus s_{(i+1)j}^{j\in L_Q} } }
-	}
-	\]
-with
-\begin{mathpar}
-\set{\gamma'_{3p}}=\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{3pj}^{j\in J_{3p}\setminus \{j_0\}}}
-
-\Pred\,'_{3p}=\Pred_{3p}\land (\beta_{3pj_0}=\alpha_i\land \Pred_i)
-
-\Post\,'_{3p} =\Post_{3p}\uplus\Post_i
-\end{mathpar}
-
-Or $j_0\not \in \dom(\beta_{3 p})$ and $Q$ does not move in the composed reduction. In this case there is no $i$ such that $p=n'_i$, but there is $i$ such that $p\in]n'_i .. n'_{i+1}[$, and
-\[P[Q]_{j_0} \models\openrule
-    {\set{\beta_{3p}},\Pred_{3p},\Post_{3p}   }
-         {\ostate{s_{3pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTarrow {\tau} \ostate{s_{3(p+1)j}^{j\in L}\uplus s_{ij}^{j\in L_Q}}}
-\]
-and thus we also have a weak OT by definition \ref{def:buildweakOT} (rule \WTDeux):
-\[P[Q]_{j_0} \models\openrule
-    {\set{\gamma'_{3p}},\Pred\,'_{3p},\Post\,'_{3p}   }
-         {\ostate{s_{3pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTWeakarrow {\tau} \ostate{s_{3(p+1)j}^{j\in L}\uplus s_{ij}^{j\in L_Q}}}
-\]
-with 
-$\set{\gamma'_{3p}}=\set{\beta_{3p}}, \Pred\,'_{3p} =\Pred_{3p}, \Post\,'_{3p} =\Post_{3p}$
-\end{enumerate}
-
-\noindent By definition of weak open transition (Definition~\ref{def:buildweakOT}, rule \WTTrois),
- we obtain:
-
-	\[ P[Q]_{j_0}  
-	\models
-	{\openrule
-		{
-			\set{\gamma'}, 
-			\Pred\,'',  \Post\,''
-			 }
-		{\ostate{s_{10j}^{j\in L}\uplus s_{0j}^{j\in L_Q}} \OTWeakarrow {\alpha''}
-			\ostate{s_{3(m_2+1)j}^{\, j\in L}\uplus s_{(n+1)j}^{j\in L_Q} } }
-	}
-	\]
-Where
-{\small 
-\begin{align*}
-\alpha''=&\alpha'{\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}\\
-\set{\gamma'}=&
- \mybigdotcup_{i=0}^{m_1}\set{\gamma'_{1i}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{1k}}\,\dotcup\,
-\set{\gamma'_{2}}\subst{\bigotimes_{k=m_1}^{0}\Post\,'_{1k}}\,\dotcup
- \mybigdotcup_{i=0}^{m_2}\set{\gamma'_{3i}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}
-\displaybreak[0]\\
-\Pred\,''=&\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\ 
-&\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_2}^{0}\Post\,'_{1j}}\displaybreak[0]\\
-\Post\,''=&\bigotimes_{j=m_2}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}
-\end{align*}
-}
-
-However it must be noticed that in steps 1 and 3, we have two kinds of WOTs with different signatures (depending on whether $Q$ moves or not).
-It is still possible to glue them together in a global rule with two more terms for $\Pred$ and $\Post$ terms.
-This global merge is possible because the post-conditions of $P$ only act on variables of $P$ and those of $Q$ on variables of $Q$ (for example $\Post_i$ has no effect on $\Pred_{1p}$ and thus does not need to be taken into account when dealing with WOTs where $Q$ does not move).
-
-We now  compare each element of the obtained WOT with the conclusion of the lemma:
-{\small \begin{align*}
-\alpha''&=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}}\\
-& = \alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}}&\text{$\alpha'$ only contains variables of $P$ untouched by $\Post_i$}\\
-& = \alpha
-\end{align*}}
-
-For $\set{\gamma'}$ we distinguish elements in the holes of $P$ and of $Q$.
-
- First suppose $j\in J\setminus\{j_0\}$ we have $\gamma'_j=\gamma_j$ because $\Post^{\,\prime}_{ij}$ has no effect on variables of $P$ and on $\beta_{1pj}$, consequently\\
-{\small \begin{equation*}
-\begin{split}\gamma'_j=&\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}}\subst{\bigotimes_{k=i-1}^{0}\! \Post_{1k} } }  \dotcup  \vis{{\beta_{2j}}\subst{\bigotimes_{k=m_1}^{0}\!\Post_{1k}}}\, \dotcup
-\mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}
-\end{split}
-\end{equation*}
-}
-
-Second, when $j\in J_t$ for some $t$,  $\gamma'_j$ is the concatenation of elements of $\gamma'_{1ij}$, $\gamma'_{2 j}$, $\gamma'_{3ij}$  that are not empty.
-By construction the concatenation of these elements is $\gamma_{tj}$, for $t\in[0..n]$.
-$\Post_{ik}$ has no effect on $\gamma_{tj}$ but  $\Post_{k}$ has.
-%\TODO{do we want to be more explicit in the explanation?
-giving the exact indices is cumbersome because Post'ij is either empty or postij for the same indices as gamma, this can also be related with the ni and n'i}
-We obtain:
-{\small\begin{equation*}
-\begin{split}
-\gamma'_j =&
-\mybigdotcup_{i=0}^{m_1}{\gamma'_{1ij}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{1k}}\dotcup
- {\gamma'_{2 j}}\subst{\bigotimes_{k=m_1}^{0}\Post\,'_{1k}}\,\dotcup\, \mybigdotcup_{i=0}^{m_2}{\gamma'_{3ij}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}\\
-=&
-{\mybigdotcup_{t=0}^{n} {\gamma_{tj}}\subst{\bigotimes_{k=t-1}^{0} \Post_{k}}}   
-\end{split}
-\end{equation*}
-}
-
-Concerning predicates, we also separate predicates on $P$ from predicates on $Q$, and from the equality on the action filling the hole:
-%\begin{small}
-%\begin{equation*}
-%\begin{split}
-%\Pred\,''&=\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\
-%&~~{\bigwedge_{i=0}^{m_3}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}}\\
-%&=\big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\
-%&~~~\bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\big) \land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i \land
-%%$~\qquad\qquad\,\displaystyle{\bigwedge_{i=0}^{m-1}(\beta_{1{n_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j={n_i}-1}^{0}\Post\,'_{1j}}\land(\beta_{2{j_0}}=\alpha_m) \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land}
-%\end{split}
-%\end{equation*}
-%%$~\qquad\qquad\,\displaystyle{\bigwedge_{i=m+1}^{n}(\beta_{3{n'_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j=n'_i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\Big)}$\\
-%\end{small}
-\begin{footnotesize}
-\begin{align*}
-\Pred\,''&=\Big(\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land%\\ &\qquad
-%~\quad
-\bigwedge_{i=0}^{m_3}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\Post\,'_{1j}}\Big)\\
-&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}\land\Pred_2\subst{\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\Big)\\&\qquad
-\land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i%\\&\qquad
-\land \Big( \bigwedge_{i=0}^{m-1}(\beta_{1{n_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j={n_i}-1}^{0}\Post\,'_{1j}}\land(\beta_{2{j_0}}=\alpha_m) \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\ &\qquad
-~\quad\bigwedge_{i=m+1}^{n}(\beta_{3{n'_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j=n'_i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\Big)\displaybreak[0]\\
-&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}\big)\land\Pred_2\subst{\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\Big)\\&\qquad
-\land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i
-\land \Big(\bigwedge_{i=0}^{m-1}(\beta_{i}=\alpha_i)\subst{\bigotimes_{j={i-1}}^{0}\Post_{j}}\land(\beta_m=\alpha_m )\subst{\bigotimes_{j=m}^{0}\Post_{j}}\land\\ &\qquad
-~\quad\bigwedge_{i=m+1}^{n}(\beta_i=\alpha_i)\subst{\bigotimes_{j=i-1}^{m}\Post_j\shortotimes\Post_m\shortotimes\bigotimes_{j=m-1}^{0}\Post_{j}}\Big)\\
-&=\Pred
-\end{align*}
-\end{footnotesize}
-
-Finally, concerning post-conditions:
-{\footnotesize \begin{equation*}
-\begin{split}
-\Post\,''&=\bigotimes_{j=m_2}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}\\
-&=\left(\bigotimes_{j=m_2}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}\right)\uplus \bigotimes_{j=n}^{0}\Post_j\\
-&=\Post \uplus \bigotimes_{j=n}^{0}\Post_j\
-\end{split}
-\end{equation*}
-}
-This allows us to conclude concerning the lemma. 
-\end{proof}
-
-%\newpage
-
-%\begin
-\noindent
-{\bf Theorem~\ref{weak-thm-congr-eq}}. \emph{Congruence}.
-	Consider an open pNet:
-	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
-	\set{\symb{SV}}\myrangle$.
-	Let $j_0\in J$ be a hole. Let $\pNetQ$ and $\pNetQ'$ be two weak FH-bisimilar pNets such that 
-	$\Sortop(\pNetQ)=\Sortop(\pNetQ')=\Sort_{j_0}$. Then 
-	$\pNet[\pNetQ]_{j_0}$ and 
-	$\pNet[\pNetQ']_{j_0}$ are weak FH-bisimilar.
-%\end{theorem}
- \begin{proof}  Consider $Q$ weak FH-bisimilar to $Q'$.
-It means that there exist a FH-bisimulation $\mathcal{R}_{Q,Q'}$ relating the two pNets $Q$ and $Q'$.
-We define a relation $\mathcal{R}$ relating states of $P[Q]_{j_0}$ with states of $P[Q']_{j_0}$:
-\[\mathcal{R} = \{(\ostate{S_P\uplus S_Q},\ostate{S_P\uplus S_{Q'}}, \Pred_{Q,Q'})|\,(S_Q,S_{Q'}, \Pred_{Q,Q'})\in\mathcal{R}_{Q,Q'}\}\]
-
-To prove weak FH-bisimulation of $\pNet[\pNetQ]_{j_0}$ and 
-	$\pNet[\pNetQ']_{j_0}$, we consider  an open transition $OT$ of $\pNet[\pNetQ]_{j_0}$, and an equivalent state of $\pNet[\pNetQ']_{j_0}$, and we try to find a family of WOT of 	$\pNet[\pNetQ']_{j_0}$ that simulates $OT$.
-Consider an OT of  $\pNet[\pNetQ]_{j_0}$ it is of the form (notations introduced to prepare the decomposition):
-\[
-\pNet[\pNetQ]_{j_0}\models\openrule
-	{
-		\beta_j^{j\in( J_P\uplus J_Q)}, 
-		\Pred_P\land \Pred_Q,  
-		\Post_P\uplus \Post_Q}
-	{\ostate{S_P\uplus S_Q} \OTarrow {\alpha}
-		\ostate{S'_P\uplus S'_Q}
-}
-\]
-
-By the decomposition lemma for OTs (Lemma~\ref{lem-decompose}), we obtain the 2 following OTs (equality side-conditions have been inlined for clarity):
-\begin{mathpar}
-%\[
-\pNet\models{\openrule
-	{
-		\beta_j^{j\in J_P}\uplus(j_0\mapsto \alpha_Q), 
-		\Pred_P,  
-		\Post_Q}
-	{\ostate{S_P} \OTarrow {\alpha}
-		\ostate{S'_P}}
-}
-\quad\text{~~and~~}\quad
-Q\models{\openrule
-	{
-		\beta_j^{j\in J_Q},
-		 \Pred_Q,  
-		\Post_Q}
-	{\ostate{S_Q} \OTarrow {\alpha_Q}
-		\ostate{S'_Q}}
-}%\]
-
-\end{mathpar}
-
-By definition of $\mathcal{R}$ we have 
-$(S_Q,S_{Q'}| \Pred_{Q,Q'})\in\mathcal{R}_{Q,Q'}$. And thus, by definition of weak FH-bisimulation, there exist a family of weak open transitions $WOT_{x}$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j x}^{j\in J_Q}, \Pred_{Q' x},\Post_{Q' x}}
-         {\ostate{S_{Q'}}\OTWeakarrow {\alpha_{x}} \ostate{S'_{Q' x}}}
-\end{mathpar}
-
-where  
-\[\forall x.\, (S'_Q,S'_{Q' x}| \Pred_{Q,Q' x})\in\mathcal{R}_{Q,Q'}\]
-
-and
-{\small%\begin{equation*}
-\begin{multline*}
-\Pred_{Q,Q'}\land \Pred_Q \implies \\
-\bigvee_{x\in X}
-(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x})\Rightarrow (\Pred_{Q_x}\land%\\ %&~~
-\alpha_Q=\alpha_x \land \Pred_{Q,Q' x}\subst{\Post_{Q' x}\uplus \Post_{Q}}) 
-\end{multline*}
-%\end{equation*}
-}
-
-Composing the OT of $P$ with the WOTs of $Q'$ by Lemma~\ref{lem-Weakcompose1} we obtain:
-\[
-\pNet[\pNetQ']_{j_0}\models\openrule
-	{
-		\vis{\beta_j^{j\in J_P}}\uplus\gamma_{j x}^{j\in J_Q}, 
-		\Pred_P\land \Pred_{Q' x},  
-		\Post_P\uplus \Post_{Q' x}}
-	{\ostate{S_P\uplus S_{Q'}} \OTWeakarrow {\alpha}
-		\ostate{S'_P\uplus S'_{Q' x}}
-}
-\]
-with $\displaystyle{\bigvee_{x\in X}
-\big(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x} \implies \alpha_Q=\alpha_x\big)}$ that ensures that the open transitions can be recomposed when the OT fires.
-
-Side conditions necessary to prove weak-FH bisimulations are:
-\[\forall x.\, (S'_P\uplus S'_Q,S'_P\uplus S'_{Q' x}| \Pred_{Q,Q' x})\in\mathcal{R}\]
-which is true, and
-\begin{multline*}
-\Pred_{Q,Q'}\land \Pred_P\land \Pred_Q \implies \\
-\Big(\bigvee_{x\in X}
-(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x}\land \forall j\in J_P.\, \vis{\beta_j}=\vis{\beta_j}))\Rightarrow \\(\Pred_P\land \Pred_{Q' x}\land \alpha=\alpha \land \Pred_{Q,Q' x}\subst{\Post_P\uplus\Post_{Q' x}\uplus \Post_{Q}}) \Big)
-\end{multline*}
-We conclude by observing that $\Post_P$ has no effect on variables of $Q$ and $Q'$, and thus on $\Pred_{Q,Q' x}$
-% OLD
-% according to Lemma  \ref{lem-alternative-weak-bisim} for any weak open transition $WOT$ in $Q$ there exist a family of weak open transitions $WOT_{x}^{x \in X}$ in $Q'$. 
-%We apply  Lemma \ref{lem-Weakcompose1} on weak open transition $WOT$, $j_0 \in J$, we obtain a new weak open transition $WOT'$ in $P[Q]_{j_0}$.
-%On other hand, we apply same Lemma \ref{lem-Weakcompose1} on each weak open transitions $WOT_{x}$, so we obtain a new family of weak open transitions $WOT_{x}'$ in $P[Q']_{j_0}$.
-%
-%Suppose we have:\\[-2ex]
-%\begin{mathpar}
-%%\[
-%P\models{\openrule
-%	{
-%		\beta_j^{j\in J}, 
-%		\Pred,  
-%		\Post}
-%	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
-%		\ostate{(s_i')^{\, i\in L}}}
-%}
-%\quad\text{~~and~~}\quad
-%Q\models{\openrule
-%	{
-%		\set{\gamma},
-%		 \Pred_Q,  
-%		\Post_Q}
-%	{\ostate{s_{i}^{i\in L_Q}} \OTWeakarrow {\alpha_Q}
-%		\ostate{(s'_{i})^{\, i\in L_Q}}}
-%}%\]
-%
-%
-%\end{mathpar}
-%
-%Then, we have by lemma \ref{lem-Weakcompose}: \\[-2ex]
-%	\[ P[Q]_{j_0}  
-%	\models
-%	{\openrule
-%		{
-%			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
-%			\Pred\,',  \Post\,'
-%			 }
-%		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
-%			\ostate{(s_i')^{\, i\in L\uplus L_Q}}}
-%	}
-%	\]
-%
-%On the other hand, $Q$ weak FH-bisimilar to $Q'$, so according to  Lemma  \ref{lem-alternative-weak-bisim} 
-%
-%such that...\\
-%
-%By applying  Lemma \ref{lem-Weakcompose} on each weak open transitions $WOT_{x}$, so we obtain a new family of weak open transitions $WOT_{x}'$ in $P[Q']_{j_0}$:
-%
-%\[ P[Q']_{j_0}  
-%	\models
-%	{\openrule
-%		{
-%			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
-%			\Pred\,',  \Post\,'
-%			 }
-%		{\ostate{s_i^{i\in L} \uplus t_{i}^{i\in L_{Q_x}}} \OTWeakarrow {\alpha}
-%			\ostate{(s_i')^{\, i\in L} \uplus t_{ix}^{i\in L_{Q_x}} }}
-%	}
-%	\]
- \end{proof}
-
-\noindent {\bf Theorem~\ref{weak-thm-ctxt-eq}}. \emph{Context equivalence}.
-	Consider two FH-bisimilar open pNets:\\
-	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
-	\set{\symb{SV}}\myrangle$ and 	$\pNet' = \mylangle {\pNet'}_i^{i\in I}, 
-	\Sort_j^{j\in 
-	J}, 	\set{\symb{SV'}}\myrangle$ 
-	(recall they must have the same holes to be bisimilar).
-	Let $j_0\in J$ be a hole, and $Q$ be a pNet such that $\Sortop(Q)=\Sort_{j_0}$. Then 
-	$\pNet[Q]_{j_0}$ and 
-	$\pNet'[Q]_{j_0}$ are FH-bisimilar.
-%\end{theorem}
-
- \begin{proof}   Consider $P$ weak FH-bisimilar to $P'$.
-There exist a FH-bisimulation $\mathcal{R}_{P,P'}$ relating $P$ and $P'$.
-We define a relation $\mathcal{R}$ relating states of $P[Q]_{j_0}$ with states of $P'[Q]_{j_0}$:
-\[\mathcal{R} = \{(\ostate{S_P\uplus S_Q},\ostate{S_{P'}\uplus S_Q}, \Pred_{P,P'})|\,(S_P,S_{P'}, \Pred_{P,P'})\in\mathcal{R}_{P,P'}\}\]
-
-To prove weak FH-bisimulation of $\pNet[\pNetQ]_{j_0}$ and 
-	$\pNet'[\pNetQ]_{j_0}$, we consider  an open transition $OT$ of $\pNet[\pNetQ]_{j_0}$, and an equivalent state of $\pNet'[\pNetQ]_{j_0}$, and we try to find a family of WOT of 	$\pNet'[\pNetQ]_{j_0}$ that simulates $OT$.
-Consider an OT of  $\pNet[\pNetQ]_{j_0}$ it is of the form (notations introduced to prepare the decomposition):
-\[
-\pNet[\pNetQ]_{j_0}\models\openrule
-	{
-		\beta_j^{j\in( J_P\uplus J_Q)}, 
-		\Pred_P\land \Pred_Q \land \Pred,  
-		\Post_P\uplus \Post_Q}
-	{\ostate{S_P\uplus S_Q} \OTarrow {\alpha}
-		\ostate{S'_P\uplus S'_Q}
-}
-\]
-
-By the decomposition lemma for OTs (Lemma~\ref{lem-decompose}), we obtain the 2 following OTs (equality side-conditions have been inlined for clarity):
-\begin{mathpar}
-%\[
-\pNet\models{\openrule
-	{
-		\beta_j^{j\in J_P}\uplus(j_0\mapsto \alpha_Q), 
-		\Pred_P,  
-		\Post_Q}
-	{\ostate{S_P} \OTarrow {\alpha}
-		\ostate{S'_P}}
-}
-\quad\text{~~and~~}\quad
-Q\models{\openrule
-	{
-		\beta_j^{j\in J_Q},
-		 \Pred_Q,  
-		\Post_Q}
-	{\ostate{S_Q} \OTarrow {\alpha_Q}
-		\ostate{S'_Q}}
-}%\]
-
-\end{mathpar}
-
-With $\Pred \iff \alpha_Q=\beta_{j_0}$
-
-By definition of $\mathcal{R}$ we have 
-$(S_P,S_{P'}, \Pred_{P,P'})\in\mathcal{R}_{P,P'}$. And thus, by definition of weak FH-bisimulation, there exist a family of weak open transitions $WOT_{x}$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j x}^{j\in J_P\uplus\{j_0\}}, \Pred_{P' x},\Post_{P' x}}
-         {\ostate{S_{P'}}\OTWeakarrow {\alpha_{x}} \ostate{S'_{P' x}}}
-\end{mathpar}
-
-where  
-\[\forall x.\, (S'_P,S'_{P' x}, \Pred_{P,P' x})\in\mathcal{R}_{P,P'}\]
-and
-\begin{equation*}
-\begin{split}
-\Pred_{P,P'}\land \Pred_P \implies &
-\Big(\bigvee_{x\in X}
-(\forall j\in J_P.\, \vis{\beta_j}=\gamma_{j x} \land \vis{\alpha_Q}=\gamma_{j_0})\Rightarrow (\Pred_{P'_x}\land\\ &~~\alpha=\alpha_x \land \Pred_{P,P' x}\subst{\Post_{P' x}\uplus \Post_{P}}) \Big)
-\end{split}
-\end{equation*}
-
-We here need a special case of Lemma~\ref{lem-Weakcompose} where the inner pNet $Q$ does a simple OT.
-This is just a particular case of the theorem but where notations get simplified because the inner pnet does a single transition.
- This way we can compose the WOTs of $P'$ with the OT of $Q$ and obtain, with $\gamma_{j_0}=[\beta] $:
-\[
-\pNet'[\pNetQ]_{j_0}\models\openrule
-	{
-		\vis{\beta_j^{j\in J_Q}}\uplus\gamma_{j x}^{j\in J_P}, 
-		\Pred_{P' x}\land \Pred_Q \land \alpha_Q=\beta,  
-		\Post_{P' x}\uplus \Post_Q}
-	{\ostate{S_{P'}\uplus S_{Q}} \OTWeakarrow {\alpha_x}
-		\ostate{{S'_{P' x}}\uplus S'_Q}
-}
-\]
-Side conditions necessary to prove weak-FH bisimulations are:
-\[\forall x.\, (S'_P\uplus S'_Q,S'_{P' x}\uplus S'_Q, \Pred_{P,P' x})\in\mathcal{R}\]
-which is true, and
-\begin{multline*}
-\Pred_{P,P'}\land \Pred_P\land \Pred_Q \Pred \implies \\
-\Big(\bigvee_{x\in X}
-(\forall j\in J_P.\, \vis{\beta_j}=\gamma_{j x} \land \forall j\in J_Q.\, \vis{\beta_j}=\vis{\beta_j} )\Rightarrow\\
- (\Pred_{P' x}\land \Pred_Q\land \alpha_Q=\beta\land  \alpha_x=\alpha \land \Pred_{P,P' x}\subst{\Post_{P' x}\uplus\Post_P\uplus \Post_{Q}}) \Big)
-\end{multline*}
-We conclude by observing that $\Post_Q$ has no effect on variables of $P$ and $P'$, and thus on $\Pred_{P,P' x}$ and $\Pred$ leading to the conclusion about $\alpha_Q=\beta$.
-\end{proof}
-
-\newpage
-
 \section{Full details of the Simple Protocol Example}
@@
        Full list of WOTs
-
-\end{document}

### 2020-06-11 2016-Weak-FH-Bisim/WeakBisim.tex
assignments
updated pNet code in appendix D

@@
         in the different terms
-       $\beta_j$ and $\alpha$. Because the variables in $V$ can be in both side of the assignments, the assignments are always applied in a parallel manner. Open transitions are identified
+       $\beta_j$ and $\alpha$. The assignments are always applied simultaneously because the variables in $V$ can be in both sides. Open transitions are identified
         modulo logical equivalence on their predicate. 
@@
 vars ?msg:Data
+vars m_msg:Data m_ec:Int
 
 state a0
-transition in(msg) -> a1 {a1_msg:=msg, m1_ec:=0}
+transition in(msg) -> a1 {m_msg:=msg, m_ec:=0}
 
 state a1
-vars a1_msg:Data m1_ec:Int
-transition out(a1_msg, m1_ec) -> a0
-transition synchro($tau)  -> a1 {m1_ec:=m1_ec+1}
+transition out(m_msg, m_ec) -> a0
+transition synchro($tau)  -> a1 {m_ec:=m_ec+1}
 
@@
   vars ?msg:Data ?c:Int
-
-state a0
-transition m_recv(msg,c) -> a1 {a1_msg:=msg, a1_ec:=c}
-
-state a1
-vars a1_msg:Data a1_ec:Int
-transition m_send(a1_msg, a1_ec) -> a0 
-transition synchro($tau) -> a2
-
-state a2
-transition $m_error -> a0
+%vars a1_msg:Data a1_ec:Int
+vars m_msg:Data m_ec:Int
+
+state m0
+transition m_recv(msg,c) -> m1 {m_msg:=msg, m_ec:=c}
+
+state m1
+transition m_send(m_msg, m_ec) -> m0 
+transition synchro($tau) -> m2
+
+state m2
+transition $m_error -> m0
 
@@
   vars ?msg:Data
+%vars s1_msg:Data s1_ec:Int
+%vars  s2_ec:Int
+vars  s_msg:Data s_ec:Int
 
 state s0
-transition s_recv(msg) -> s1 {s1_msg:=msg, s1_ec:=0}
+transition s_recv(msg) -> s1 {s_msg:=msg, s_ec:=0}
 
 state s1
-vars s1_msg:Data s1_ec:Int
-transition s_send(s1_msg, s1_ec) -> s2 {s2_ec:=s1_ec}
+transition s_send(s_msg, s_ec) -> s2
 
 state s2
-vars  s2_ec:Int
 transition $s_ack -> s0
-transition $s_error -> s1 {s1_ec:=s2_ec+1}
+transition $s_error -> s1 {s_ec:=s_ec+1}
 
@@
   vars ?msg:Data ?c:Int
+%vars r1_msg:Data r1_ec:Int
+vars r_msg:Data r_ec:Int
 
 state r0
-transition r_recv(msg,c) -> r1 {r1_msg:=msg, r1_ec:=c}
+transition r_recv(msg,c) -> r1 {r_msg:=msg, r_ec:=c}
 
 state r1
-vars r1_msg:Data r1_ec:Int
-transition r_send(r1_msg, r1_ec) -> r2
+transition r_send(r_msg, r_ec) -> r2
 
@@
 
-\TODO{To be updated completely}
+\TODO{To be updated completely, or removed ???}
 

### 2020-06-12 2016-Weak-FH-Bisim/WeakBisim.tex
Changes pages 22 and 73-76

@@
 = (\texttt{s\_ec}\gets \texttt{s\_ec}+1)$.
-\footnote{when showing  the result of $Posts$ composition, we will Z omit the identity substitutions introduced by the $\shortotimes$ definition in page \pageref{def:substitutions}}
+\footnote{when showing  the result of $Posts$ composition, we will omit the identity substitutions introduced by the $\shortotimes$ definition in page \pageref{def:substitutions}}
 \medskip
@@
 We can now show some of the weak OTs of Figure \ref{SimpleProtCounter:ImplWOA2} (the full table is included in Appendix \ref{Appendix:FullExample}) :
-
-\TODO{Qu'est-ce qu'on avait dit ici pour "$n$" ? a droite ou a gauche, mais pas les deux ?Et est-ce qu'on le laisse en italique dans les expressions, pour souligner son statut de parametre ?.
-Dans tous les cas expliquer ?}
+As we have seen above, the effect of rule $WT_3$ when a silent action have an effect on the variable $ec$ will generate an infinite family of WOTs, depending on the number of iterations through the loops.
+We denote these families using a "meta-variable" $n$, ranging over $\mathcal{N}$.
+% \TODO{Qu'est-ce qu'on avait dit ici pour "$n$" ? a droite ou a gauche, mais pas les deux ?Et est-ce qu'on le laisse en italique dans les expressions, pour souligner son statut de parametre ?.
+% Dans tous les cas expliquer ?}
 \smallskip
@@
 
-$ WI_3(n) = \openrule
+$ \forall n\ge 0. WI_3(n) = \openrule
   {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
@@
   {000 \OTWeakarrow {\nounderline{\texttt{in(m)}}} 100}
-        $$\forall n\ge 0$
-
-$ WI_4(n) = \openrule
+        $
+
+$  \forall n\ge 0. WI_4(n) = \openrule
          {\{\}, True, 
@@
          {100 \OTWeakarrow {\tau} 210}
-        $$\forall n\ge 0$
-
-$ WI_{456}(n) = \openrule
+        $
+
+$  \forall n\ge 0. WI_{456}(n) = \openrule
          {\{\}, True, 
@@
   {100 \OTWeakarrow {\tau} 100}
-        $$\forall n\ge 0$
+        $
 
    \medskip     
-The  \Post~of of the weak OT $ WI_{6a}$ is:\\
+The  \Post~of the weak OT $ WI_{6a}$ is:\\
 
@@
 \begin{array}{ll}
-Post_{6a}= post_{4}\shortotimes\ post_{456*}\shortotimes\ post_{6} =&  (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec})\,
-\shortotimes \\ &(\texttt{s\_ec}\gets \texttt{s\_ec}+n) 
-\shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+1) =\\
-&(\texttt{m\_msg}\!\gets \texttt{s\_msg}, \texttt{m\_ec}\!\gets \texttt{s\_ec}+1\!+\!n, \texttt{s\_ec}\!\gets \texttt{s\_ec}+1\!+\!n)
-\end{array}$\\
-
-\begin{align*}
-WI_{6a}(n) =& \openrule
+Post_{6a}&= post_{4}\shortotimes\ post_{456*}\shortotimes\ post_{6}\\ 
+&=  (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec})\,
+\shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+n) 
+\shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+1) \\
+&= (\texttt{m\_msg}\!\gets \texttt{s\_msg}, \texttt{m\_ec}\!\gets \texttt{s\_ec}+1\!+\!n, \texttt{s\_ec}\!\gets \texttt{s\_ec}+1\!+\!n)
+\end{array}
+$
+
+So we get:
+
+$ \forall n\ge 0. WI_{6a}(n) = \openrule
          {\{\}, True, 
-         (\texttt{m\_ec}\gets \texttt{s\_ec}+1+n, \texttt{s\_ec}\gets \texttt{s\_ec}+n)}
-         {220 \OTWeakarrow {\tau} 210} \forall n\ge 0
-\\Post_{8c}=& post_{8}\shortotimes\ post_{7}\shortotimes\ post_{4}\shortotimes\ post_{456*} 
-= (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_msg}+1+n), \forall n\ge 0\\ 
-WI_{8c}(n) =& \openrule
-         {\{\texttt{Q}\mapsto \texttt{q-recv(s\_msg,s\_ec}+n)\}, True, (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_msg}+1+n)}
-         {210 \OTWeakarrow {\nounderline{\texttt{out(s\_msg,s\_ec}+n)}} 202}\forall n\ge 0
-\end{align*}
+         (\texttt{m\_ec}\gets \texttt{s\_ec}+1+n, \texttt{s\_ec}\gets \texttt{s\_ec}+1+n)}
+         {220 \OTWeakarrow {\tau} 210}$
+
+%\begin{align*}
+%\\Post_{8c}=& post_{8}\shortotimes\ post_{7}\shortotimes\ post_{4}\shortotimes\ post_{456*} 
+%= (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_msg}+1+n), \forall n\ge 0\\ 
+%WI_{8c}(n) =& \openrule
+  %       {\{\texttt{Q}\mapsto \texttt{q-recv(s\_msg,s\_ec}+n)\}, True, (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_msg}+1+n)}
+   %      {210 \OTWeakarrow {\nounderline{\texttt{out(s\_msg,s\_ec}+n)}} 202}\forall n\ge 0
+%\end{align*}
 
@@
 
-\TODO{Je ne peux pas refaire tourner le code, il faut que je modifie le pNet Editor pour qu'ils n'utilise plus les variables d'etat... Donc les 3 prochaines pages sont obsoletes...}
+%\TODO{Je ne peux pas refaire tourner le code, il faut que je modifie le pNet Editor pour qu'ils n'utilise plus les variables d'etat... Donc les 3 prochaines pages sont obsoletes...}
 %% \TODO{keep ?}
@@
   vars ?msg:Data ?c:Int
-%vars a1_msg:Data a1_ec:Int
 vars m_msg:Data m_ec:Int
@@
   vars ?msg:Data
-%vars s1_msg:Data s1_ec:Int
-%vars  s2_ec:Int
 vars  s_msg:Data s_ec:Int
@@
   vars ?msg:Data ?c:Int
-%vars r1_msg:Data r1_ec:Int
 vars r_msg:Data r_ec:Int
@@
 
-Finaly, we list here in raw format, the 19 OTs computed by the tool for the SimpleProtImpl pNet.
-This view uses variable names very close to the internal representation in the tool, allowing for traceability of generated fresh variables. For example:
-\begin{itemize}
-\item m:SV6:1:1 refers to a variable named ``m'' in the synchronisation vector ``SV6''; the last 2 numbers allows to distinguish different clones.
-\item the other variable names reflect our naming policy: state variables are prefixed by the name of the state, holes actions by the name of the hole.
-\end{itemize}
-
-\TODO{To be updated completely, or removed ???}
-
-\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
-
-{P|->p_send(m:SV6:1:1)},
-[(msg=m:SV0:12:1)/\((s_recv(msg))=(s_recv(m:SV0:12:1)))], {s1_msg := msg, s1_ec := 0}
-	OT:1 ------------------------------------------------------------
-		<s0_a0_r0>-----_in(m:SV6:1:1)_----><s1_a0_r0>
-
-{P|->p_a:SV7:1:2},
-[(forall:m:SV7:1:2. (p_a:SV7:1:2!=(p_send(m:SV7:1:2)))], {}
-	OT:2 ------------------------------------------------------------
-		<s0_a0_r0>-----p_a:SV7:1:2----><s0_a0_r0>
-
-{Q|->q_a:SV9:1:4},
-[(forall:m:SV9:1:4,c:SV9:1:4. (q_a:SV9:1:4!=(q_recv(m:SV9:1:4, c:SV9:1:4)))],   {}
-	OT:3 ------------------------------------------------------------
-		<s0_a0_r0>-----q_a:SV9:1:4----><s0_a0_r0>
-
-INFO  SimpleProtImpl2 - 
-{P|->p_a:SV7:1:2},
-[(forall:m:SV7:1:2. (p_a:SV7:1:2!=(p_send(m:SV7:1:2)))],   {}
-	OT:4 ------------------------------------------------------------
-		<s1_a0_r0>-----p_a:SV7:1:2----><s1_a0_r0>
-
-{Q|->q_a:SV9:1:4},
-[(forall:m:SV9:1:4,c:SV9:1:4. (q_a:SV9:1:4!=(q_recv(m:SV9:1:4, c:SV9:1:4)))],   {}
-	OT:5 ------------------------------------------------------------
-		<s1_a0_r0>-----q_a:SV9:1:4----><s1_a0_r0>
-
-{},   [(s1_msg=m:SV1:114:2)/\(s1_ec=c:SV1:114:2)
-  /\((s_send(s1_msg, s1_ec))=(s_send(m:SV1:114:2, c:SV1:114:2)))
-  /\(msg=m:SV1:114:2)/\(c=c:SV1:114:2)
-  /\((m_recv(msg, c))=(m_recv(m:SV1:114:2, c:SV1:114:2)))],
-{s2_ec := s1_ec, a1_msg := msg, a1_ec := c}
-	OT:6 ------------------------------------------------------------
-		<s1_a0_r0>-----_tau_----><s2_a1_r0>
-
-{P|->p_a:SV7:1:2},
-[(forall:m:SV7:1:2. (p_a:SV7:1:2!=(p_send(m:SV7:1:2)))],   {}
-	OT:7 ------------------------------------------------------------
-		<s2_a1_r0>-----p_a:SV7:1:2----><s2_a1_r0>
-
-{Q|->q_a:SV9:1:4},
-[(forall:m:SV9:1:4,c:SV9:1:4. (q_a:SV9:1:4!=(q_recv(m:SV9:1:4, c:SV9:1:4)))],   {}
-	OT:8 ------------------------------------------------------------
-		<s2_a1_r0>-----q_a:SV9:1:4----><s2_a1_r0>
-
-{},   [(a1_msg=m:SV2:114:3)/\(a1_ec=c:SV2:114:3)
-  /\((m_send(a1_msg, a1_ec))=(m_send(m:SV2:114:3, c:SV2:114:3)))
-  /\(msg=m:SV2:114:3)/\(c=c:SV2:114:3)
-  /\((r_recv(msg, c))=(r_recv(m:SV2:114:3, c:SV2:114:3)))],
-{r1_msg := msg, r1_ec := c}
-	OT:9 ------------------------------------------------------------
-		<s2_a1_r0>-----_tau_----><s2_a0_r1>
-
-		{},   [],   {}
-	OT:10 ------------------------
-		<s2_a1_r0>-----_tau_----><s2_a2_r0>
-
-{P|->p_a:SV7:1:2},
-[(forall:m:SV7:1:2. (p_a:SV7:1:2!=(p_send(m:SV7:1:2)))],   {}
-	OT:11 ------------------------------------------------------------
-		<s2_a0_r1>-----p_a:SV7:1:2----><s2_a0_r1>
-
-{Q|->q_recv(m:SV8:1:3, c:SV8:1:3)},
-[(r1_msg=m:SV5:18:6)/\(r1_ec=c:SV5:18:6)
-  /\((r_send(r1_msg, r1_ec))=(r_send(m:SV5:18:6, c:SV5:18:6)))],   {}
-	OT:12 ------------------------------------------------------------
-		<s2_a0_r1>-----_out(m:SV8:1:3, c:SV8:1:3)_----><s2_a0_r2>
-
-{Q|->q_a:SV9:1:4},
-[(forall:m:SV9:1:4,c:SV9:1:4. (q_a:SV9:1:4!=(q_recv(m:SV9:1:4, c:SV9:1:4)))],   {}
-	OT:13 ------------------------------------------------------------
-		<s2_a0_r1>-----q_a:SV9:1:4----><s2_a0_r1>
-
-{P|->p_a:SV7:1:2},
-[(forall:m:SV7:1:2. (p_a:SV7:1:2!=(p_send(m:SV7:1:2)))],   {}
-	OT:14 ------------------------------------------------------------
-		<s2_a2_r0>-----p_a:SV7:1:2----><s2_a2_r0>
-
-{Q|->q_a:SV9:1:4},
-[(forall:m:SV9:1:4,c:SV9:1:4. (q_a:SV9:1:4!=(q_recv(m:SV9:1:4, c:SV9:1:4)))],   {}
-	OT:15 ------------------------------------------------------------
-		<s2_a2_r0>-----q_a:SV9:1:4----><s2_a2_r0>
-
-		{},   [],   {s1_ec := s2_ec+1}
-	OT:16 --------------------------------------
-		<s2_a2_r0>-----_tau_----><s1_a0_r0>
-
-{P|->p_a:SV7:1:2},
-[(forall:m:SV7:1:2. (p_a:SV7:1:2!=(p_send(m:SV7:1:2)))],   {}
-	OT:17 ------------------------------------------------------------
-		<s2_a0_r2>-----p_a:SV7:1:2----><s2_a0_r2>
-
-{Q|->q_a:SV9:1:4},
-[(forall:m:SV9:1:4,c:SV9:1:4. (q_a:SV9:1:4!=(q_recv(m:SV9:1:4, c:SV9:1:4)))],   {}
-	OT:18 ------------------------------------------------------------
-		<s2_a0_r2>-----q_a:SV9:1:4----><s2_a0_r2>
-
-		{},   [],   {}
-	OT:19 ------------------------
-		<s2_a0_r2>-----_tau_----><s0_a0_r0>
-
-Assignements of state variables:
-
-Global State: <s0_a0_r0>
-===================
-pLTS States: <s0 vars: {}> <a0 vars: {}> <r0 vars: {}>
-
-Global State: <s1_a0_r0>
-===================
-pLTS States: <s1 vars: { s1_msg <-{msg} s1_ec <-{0, s2_ec+1}}> <a0 vars: {}> <r0 vars: {}>
-
-Global State: <s2_a1_r0>
-===================
-pLTS States: <s2 vars: { s2_ec <-{s1_ec}}> <a1 vars: { a1_msg <-{msg} a1_ec <-{c}}> <r0 vars: {}>
-
-Global State: <s2_a0_r1>
-===================
-pLTS States: <s2 vars: { s2_ec <-{s1_ec}}> <a0 vars: {}> <r1 vars: { r1_ec <-{c} r1_msg <-{msg}}>
-
-Global State: <s2_a2_r0>
-===================
-pLTS States: <s2 vars: { s2_ec <-{s1_ec}}> <a2 vars: {}> <r0 vars: {}>
-
-Global State: <s2_a0_r2>
-===================
-pLTS States: <s2 vars: { s2_ec <-{s1_ec}}> <a0 vars: {}> <r2 vars: {}>
-
-INFO  SimpleProtImpl2 - Total: 19 SATISFIABLE OTs
-INFO  SimpleProtImpl2 -        185 UNSATISFIABLE OTs
-INFO  SimpleProtImpl2 - Total Time: 1105 ms
-
-\end{lstlisting}
-
 %% And here is a  drawing of this open automaton, slightly simplified for readability:
@@
 equivalence class of states as $\{000,202\}$.
-\TODO{May be express this property more formerly, but this could be also part of another paper, more oriented towards algorithms and optimisation of the Weak}
-
-Details of the weak transitions is listed here:
+
+% \TODO{May be express this property more formerly, but this could be also part of another paper, more oriented towards algorithms and optimisation of the Weak}
+
+Full details of the weak transitions is listed here:
 
@@
 
-All following transitions are parametrized by an arbitrary non-negative integer $n\in \mathcal{N}$.
+All the following transitions are parametrized by an integer $n\in \mathcal{N}$, meaning they stand for the (infinite) set of weak OTs. 
+In some cases, this set is further restricted (see e.g. $WI_{7b}(n)$), in which case we have added an explicit quantifier.
+\smallskip
 
@@
          {210 \OTWeakarrow {\tau} 220}
-         \ \forall n\ge 0$
+         $
 
@@
          {210 \OTWeakarrow {\tau} 100}
-         \ \forall n\ge 0$
+         $
 
@@
          {210 \OTWeakarrow {\tau} 201}
-         \ \forall n\ge 0$
+         $
 
@@
          {220 \OTWeakarrow {\tau} 201}
-         \ \forall n\ge 0$
-
-$ WI_{7b}(n) = \openrule
+         $
+
+$ \forall n\ge 1. WI_{7b}(n) = \openrule
          {\{\}, True, (\texttt{r\_msg}\gets \texttt{m\_msg}, \texttt{r\_ec}\gets \texttt{s\_ec}+n)}
          {100 \OTWeakarrow {\tau} 201}
-         \ \forall n\ge 1$
+         $
 
@@
          {201 \OTWeakarrow {\nounderline{\texttt{out(r1-msg,r1-ec)}}} \{202, 000\}}
-         \ \forall n\ge 0$
-
-$ WI_{8a}(n) = \openrule
+         $
+
+$ \forall n\ge 1. WI_{8a}(n) = \openrule
          {\{\texttt{Q}\mapsto \texttt{q-recv(m\_msg,m\_ec}+n)\}, True, ()}
          {210 \OTWeakarrow {\nounderline{\texttt{out(m\_msg,m\_ec}+n)}} \{202, 000\}}
-         \ \forall n\ge 1$
-
- $ WI_{8b}(n) = \openrule
+         $
+
+ $ \forall n\ge 1.  WI_{8b}(n) = \openrule
          {\{\texttt{Q}\mapsto \texttt{q-recv(??\_msg,s\_ec}+n)\}, True, ()}
          {220 \OTWeakarrow {\nounderline{\texttt{out(??\_msg,m\_ec}+n)}} \{202, 000\}}
-         \ \forall n\ge 1$
-
- $ WI_{8c}(n) = \openrule
+         $
+
+ $ \forall n\ge 1.  WI_{8c}(n) = \openrule
          {\{\texttt{Q}\mapsto \texttt{q-recv(s\_msg,s\_ec}+n)\}, True, ()}
          {100 \OTWeakarrow {\nounderline{\texttt{out(s\_msg,s\_ec}+n)}} \{202, 000\}}
-         \ \forall n\ge 1$
+         $
 
@@
 \bigskip
-Considering the first triple <b0, 000, True>, we will prove the following properties, in which $OT<<WOT$ means that the (strong) open transition $OT$ is covered, in the sense of definition \ref{def-Weak-bisim} by the weak transition $WOT$ (it could be a set, but this will not be used here):
+Considering the first triple <b0, 000, True>, we have to prove the following properties, in which $OT<<WOT$ means that the (strong) open transition $OT$ is covered, in the sense of definition \ref{def-Weak-bisim}, by the weak transition $WOT$ (it could be a set, but this will not be used here):
 
@@
 
-       Full list of WOTs
-
 \end{document}

### 2020-06-16 2016-Weak-FH-Bisim/WeakBisim.tex
clean up to page 26
only the last appendix still pending...

@@
       sub-net are of the form ``$< -, \tau, -> -> \tau$''.
-    \item We must take care of variable name conflicts: in our example, the state variables of the 2 systems already have different names, but the action parameters occurring in the transitions (m, msg, ec) are the same, that is not correct.
+    \item We must take care of variable name conflicts: in our example, the variables of the 2 systems already have different names, but the action parameters occurring in the transitions (m, msg, ec) are the same, that is not correct.
 In the tools, this is managed by the static semantic layer; in the following example, we have renamed all conflicting variables with 1 for the Spec, and 2 for the Impl.
@@
   Checking that $\mathcal{R}$ is a weak FH-Bisimulation means checking, for each of these triples, that each (strong) OT of one the states corresponds to a set of WOTs of the other, using the conditions from Definition \ref{def-Weak-bisim}.
-  We give here two examples.
-
-  \medskip
-  Consider the second triple from the table, and transition $SS_3$ from state $b0$. Its easy to guess that it will correspond to $WI_3(0)$ of $202$.
+  We give here one  example: consider the second triple from the table, and transition $SS_3$ from state $b0$. Its easy to guess that it will correspond to $WI_3(0)$ of state $202$.
 
@@
 
-  Let check formally the conditions:
+  Let us check formally the conditions:
 
@@
 
-\end{itemize}
-
-  \bigskip
-  Now consider the $3^{rd}$ triple from the table, and transition $SI_{4}$ from state $100$ to state $210$. It should correspond to $WS_4(0)$ of $b1$, where:
-
-  $ SI_{4} = \openrule
-         {\{\}, True, (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec}, \texttt{s\_ec}\gets \texttt{s\_ec})}
-         {100 \OTarrow {\tau} 210}
-         $
-
-  $ WS_4(n) = \openrule
-         {\{\}, True, (\texttt{b\_ec}\gets \texttt{b\_ec}+n)}
-         {\text{b1} \OTWeakarrow {\tau} \text{b1}}
-         \ \forall n\ge 0
-         $
-
-  \medskip       A similar reasonning gives us
-\begin{itemize}
-  \item No active holes and the pair of ressulting states $<210,b1>$ is in $\mathcal{R}$.
-\item $fv(SI_4) = \{\}, fv(WS_4(n)) = \{n\}$,
-\item and the verification condition\\
-
-         $(\texttt{b\_msg} = \texttt{s\_msg} \land \texttt{b\_ec} = \texttt{s\_ec}) \land True\hspace{3mm} \implies
-\exists n.(True \land \tau=\tau \land \\ (\texttt{b\_msg} = \texttt{m\_msg} \land \texttt{b\_ec} = \texttt{m\_ec})  \subst{\texttt{m\_msg}\!\gets\!
-\texttt{s\_msg}, \texttt{m\_ec}\!\gets\!
-\texttt{s\_ec}, \texttt{s\_ec}\gets \texttt{s\_ec}}
-\uplus \subst{\texttt{b\_ec}\gets \texttt{b\_ec}+n})
-$
-
-is easily proved True for $n=0$.
 \end{itemize}
@@
 
-         Note: if we were using the alternative Weak bisim from Appendix \ref{app-WFH-equiv}, Lemma \ref{lem-rel-OT-WOT}, we would have a lot more transitions to examine, as we  have 4 weak transitions for $b0$ in the specification weak automaton, but 7 WOTs from 000 in the implementation automaton.
+         Note: if we were using the alternative Weak bisim from Appendix \ref{app-WFH-equiv}, Lemma \ref{lem-rel-OT-WOT}, that is checking strong bisimulation between the corresponding 
+weak automata, we would have a lot more transitions to examine, as we  have 4 weak transitions for $b0$ in the specification weak automaton, and 7 WOTs from 000 in the implementation automaton.
+
+Preliminary remarks:
+  \begin{itemize}
+    \item Both pNets trivialy verify the ``non-observability''
+      condition: the only vectors having $\tau$ as an action of a
+      sub-net are of the form ``$< -, \tau, -> -> \tau$''.
+    \item We must take care of variable name conflicts: in our example, the variables of the 2 systems already have different names, but the action parameters occurring in the transitions (m, msg, ec) are the same, that is not correct.
+In the tools, this is managed by the static semantic layer; in the following example, we have renamed all conflicting variables with 1 for the Spec, and 2 for the Impl.
+    \end{itemize}
+
+  \medskip
+We will check here 2 of these conditions, starting with the first one: $SS_1 << WI_1$
+
+  $ SS_1 = \openrule
+  {\{\texttt{P}\mapsto \texttt{p-send(m1)}\}, True,
+    (\texttt{b\_msg}\gets \texttt{m1}, \texttt{b\_ec}\gets 0)}
+  {\text{b0} \OTarrow {\nounderline{\texttt{in(m1)}}} \text{b1}}
+  $
+
+$ WI_3(0) = \openrule
+  {\{\texttt{P}\mapsto \texttt{p-send(m2)}\}, True,
+    (\texttt{s\_msg}\gets \texttt{m2}, \texttt{s\_ec}\gets 0)}
+  {000 \OTWeakarrow {\nounderline{\texttt{in(m2)}}} 100}
+  $
+
+  Let check formally the conditions:
+
+\begin{itemize}
+  \item Their sets of active (non-silent) holes is the same: $J' = J_x = \{\texttt{P}\}$.
+  \item Triple ($\text{b1},  100,  \texttt{b\_msg = s\_msg} \land \texttt{b\_ec = s\_ec}$) is in $\mathcal{R}$.
+  \item The verification condition \\
+    $\forall fv_{OT}. \{ \Pred \land \Pred_{OT}\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
+   \left[\exists fv_{OT_x}.
+  \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
+     \!\land\! \alpha\!=\!\alpha_x\! \land\!  
+     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)\right]\}}$
+
+\medskip Gives us:
+
+$\forall \texttt{m1}. \{True \land True\hspace{3mm} \implies
+\exists \texttt{m2}. \\
+(\texttt{[p-send(m1)]} = \texttt{[p-send(m2)]}
+\land True
+\land \nounderline{\texttt{in(m1)}} = \nounderline{\texttt{in(m2)}} \land 
+\\
+(\texttt{b\_msg\!\!
+= \!\!s\_msg} \land \texttt{b\_ec\!\!
+=\!\!
+s\_ec}) \subst{(\texttt{b\_msg}\!\gets\!
+\texttt{m1}, \texttt{b\_ec}\!\gets\!
+0)\uplus (\texttt{s\_msg}\!\gets\!
+\texttt{m2},\texttt{s\_ec}\!\gets\!
+0)})\}$
+
+\medskip That reduces to:
+
+$\forall \texttt{m1}. \exists \texttt{m2}.
+(\texttt{p-send(m1)} = \texttt{p-send(m2)}
+\land \texttt{in(m1)} = \texttt{in(m2)}
+\land \texttt{m1}=\texttt{m2} \land 0=0)$
+
+\medskip That is a tautology.
+
+\end{itemize}
+
+  \bigskip
+  Now consider the $3^{rd}$ triple from the table, and transition $SI_{4}$ from state $100$ to state $210$. It should correspond to $WS_4(0)$ of $b1$, where:
+
+  $ SI_{4} = \openrule
+         {\{\}, True, (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec}, \texttt{s\_ec}\gets \texttt{s\_ec})}
+         {100 \OTarrow {\tau} 210}
+         $
+
+  $ WS_4(n) = \openrule
+         {\{\}, True, (\texttt{b\_ec}\gets \texttt{b\_ec}+n)}
+         {\text{b1} \OTWeakarrow {\tau} \text{b1}}
+         \ \forall n\ge 0
+         $
+
+  \medskip       A similar reasonning gives us
+\begin{itemize}
+  \item No active holes and the pair of ressulting states $<210,b1>$ is in $\mathcal{R}$.
+\item $fv(SI_4) = \{\}, fv(WS_4(n)) = \{n\}$,
+\item and the verification condition\\
+
+         $(\texttt{b\_msg} = \texttt{s\_msg} \land \texttt{b\_ec} = \texttt{s\_ec}) \land True\hspace{3mm} \implies
+\exists n.(True \land \tau=\tau \land \\ (\texttt{b\_msg} = \texttt{m\_msg} \land \texttt{b\_ec} = \texttt{m\_ec})  \subst{\texttt{m\_msg}\!\gets\!
+\texttt{s\_msg}, \texttt{m\_ec}\!\gets\!
+\texttt{s\_ec}, \texttt{s\_ec}\gets \texttt{s\_ec}}
+\uplus \subst{\texttt{b\_ec}\gets \texttt{b\_ec}+n})
+$
+
+is easily proved True for $n=0$.
+ \end{itemize}
 

### 2020-06-16 2016-Weak-FH-Bisim/WeakBisim.tex
correction page 72-73
Finie ??

@@
 
-\tableofcontents
+% \tableofcontents
 
@@
     \end{tabular}
+
     \bigskip
@@
 \bigskip
-Considering the first triple <b0, 000, True>, we have to prove the following properties, in which $OT<<WOT$ means that the (strong) open transition $OT$ is covered, in the sense of definition \ref{def-Weak-bisim}, by the weak transition $WOT$ (it could be a set, but this will not be used here):
+Consider the first triple <b0, 000, True>, we have to prove the following 6 properties, in which $OT<<WOT$ means that the (strong) open transition $OT$ is covered, in the sense
+of definition \ref{def-Weak-bisim}, by the weak transition $WOT$ (it could be a set, but this will not be used here):
 
 \bigskip
+\begin{minipage}{0.2\linewidth} 	 
 $SS_1 << WI_1$
@@
 $SS_3 << WI_3$
-
-\smallskip
+\end{minipage}
+\hspace{1cm}
+\begin{minipage}{0.4\linewidth}
 $SI_1 << WS_1$
@@
 $SI_3 << WS_3$
+\end{minipage}
+
+\bigskip
 
          Note: if we were using the alternative Weak bisim from Appendix \ref{app-WFH-equiv}, Lemma \ref{lem-rel-OT-WOT}, that is checking strong bisimulation between the corresponding 
-weak automata, we would have a lot more transitions to examine, as we  have 4 weak transitions for $b0$ in the specification weak automaton, and 7 WOTs from 000 in the implementation automaton.
-
+weak automata, we would have a more transitions coverage to examine, as we have 4 weak transitions for $b0$ in the specification weak automaton, and 7 WOTs (including 4 
+parameterized WOTs) from 000 in the implementation automaton.
+
+We will check here 2 of these conditions.
 Preliminary remarks:
@@
       sub-net are of the form ``$< -, \tau, -> -> \tau$''.
-    \item We must take care of variable name conflicts: in our example, the variables of the 2 systems already have different names, but the action parameters occurring in the transitions (m, msg, ec) are the same, that is not correct.
-In the tools, this is managed by the static semantic layer; in the following example, we have renamed all conflicting variables with 1 for the Spec, and 2 for the Impl.
+    \item We must take care of variable name conflicts: in our example, the variables of the 2 systems already have different names, but the action parameters occurring in the 
+transitions (m, msg, ec) are the same, that is not correct. In the tools, this is managed by the static semantic layer; in the following example, we have renamed all conflicting 
+variables using suffix 1 for the Specification, and 2 for the Implementation.
     \end{itemize}
@@
   \medskip
-We will check here 2 of these conditions, starting with the first one: $SS_1 << WI_1$
+Let us start with the first pair: $SS_1 << WI_1$, where:
 
   $ SS_1 = \openrule
-  {\{\texttt{P}\mapsto \texttt{p-send(m1)}\}, True,
-    (\texttt{b\_msg}\gets \texttt{m1}, \texttt{b\_ec}\gets 0)}
-  {\text{b0} \OTarrow {\nounderline{\texttt{in(m1)}}} \text{b1}}
+  {\{\texttt{P}\mapsto \texttt{p-a1}\}, 
+ [\forall \texttt{m1}. \texttt{p-a1} \neq \texttt{p-send(m1)} ], ()}
+  {\text{b0} \OTarrow {\nounderline{\texttt{p-a1}}} \text{b0}}
   $
 
-$ WI_3(0) = \openrule
-  {\{\texttt{P}\mapsto \texttt{p-send(m2)}\}, True,
-    (\texttt{s\_msg}\gets \texttt{m2}, \texttt{s\_ec}\gets 0)}
-  {000 \OTWeakarrow {\nounderline{\texttt{in(m2)}}} 100}
-  $
+$ WI_1 = \openrule
+  {\{\texttt{P}\mapsto \texttt{p-a2}\}, 
+ [\forall \texttt{m2}. \texttt{p-a2} \neq \texttt{p-send(m2)} ], ()}
+{000 \OTWeakarrow {\texttt{p-a2}} 000}$
 
@@
   \item Their sets of active (non-silent) holes is the same: $J' = J_x = \{\texttt{P}\}$.
-  \item Triple ($\text{b1},  100,  \texttt{b\_msg = s\_msg} \land \texttt{b\_ec = s\_ec}$) is in $\mathcal{R}$.
+  \item Triple ($\text{b0},  000,  True$) is in $\mathcal{R}$.
   \item The verification condition \\
@@
 
-$\forall \texttt{m1}. \{True \land True\hspace{3mm} \implies
-\exists \texttt{m2}. \\
-(\texttt{[p-send(m1)]} = \texttt{[p-send(m2)]}
-\land True
-\land \nounderline{\texttt{in(m1)}} = \nounderline{\texttt{in(m2)}} \land 
-\\
-(\texttt{b\_msg\!\!
-= \!\!s\_msg} \land \texttt{b\_ec\!\!
-=\!\!
-s\_ec}) \subst{(\texttt{b\_msg}\!\gets\!
-\texttt{m1}, \texttt{b\_ec}\!\gets\!
-0)\uplus (\texttt{s\_msg}\!\gets\!
-\texttt{m2},\texttt{s\_ec}\!\gets\!
-0)})\}$
-
-\medskip That reduces to:
-
-$\forall \texttt{m1}. \exists \texttt{m2}.
-(\texttt{p-send(m1)} = \texttt{p-send(m2)}
-\land \texttt{in(m1)} = \texttt{in(m2)}
-\land \texttt{m1}=\texttt{m2} \land 0=0)$
-
-\medskip That is a tautology.
+$\forall \texttt{p-a1}. \{True \land \forall \texttt{m1}. \texttt{p-a1} \neq \texttt{p-send(m1)}\\
+ \hspace{3mm} \implies \exists \texttt{pa-2}. 
+(\texttt{p-a1} = \texttt{p-a2}
+\land \forall \texttt{m2}. \texttt{p-a2} \neq \texttt{p-send(m2)}
+\land \nounderline{\texttt{p-a1}} = \nounderline{\texttt{p-a2}} 
+\land True\}$
+
+\medskip That is trivialy true, choosing pa-2 = pa-1 for each p-a1.
 
@@
   \bigskip
-  Now consider the $3^{rd}$ triple from the table, and transition $SI_{4}$ from state $100$ to state $210$. It should correspond to $WS_4(0)$ of $b1$, where:
-
-  $ SI_{4} = \openrule
-         {\{\}, True, (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec}, \texttt{s\_ec}\gets \texttt{s\_ec})}
-         {100 \OTarrow {\tau} 210}
-         $
-
-  $ WS_4(n) = \openrule
-         {\{\}, True, (\texttt{b\_ec}\gets \texttt{b\_ec}+n)}
-         {\text{b1} \OTWeakarrow {\tau} \text{b1}}
-         \ \forall n\ge 0
-         $
-
-  \medskip       A similar reasonning gives us
-\begin{itemize}
-  \item No active holes and the pair of ressulting states $<210,b1>$ is in $\mathcal{R}$.
-\item $fv(SI_4) = \{\}, fv(WS_4(n)) = \{n\}$,
-\item and the verification condition\\
-
-         $(\texttt{b\_msg} = \texttt{s\_msg} \land \texttt{b\_ec} = \texttt{s\_ec}) \land True\hspace{3mm} \implies
-\exists n.(True \land \tau=\tau \land \\ (\texttt{b\_msg} = \texttt{m\_msg} \land \texttt{b\_ec} = \texttt{m\_ec})  \subst{\texttt{m\_msg}\!\gets\!
-\texttt{s\_msg}, \texttt{m\_ec}\!\gets\!
-\texttt{s\_ec}, \texttt{s\_ec}\gets \texttt{s\_ec}}
-\uplus \subst{\texttt{b\_ec}\gets \texttt{b\_ec}+n})
-$
-
-is easily proved True for $n=0$.
- \end{itemize}
+  All others pairs from this set are just as trivialy prove true.
 

### 2020-07-03 2016-Weak-FH-Bisim/WeakBisim.tex
Update WeakBisim.tex
ooops, clean annexe D

@@
 \subsubsection*{Running example}
+\label{subsubsection:runnig example}
 In Section~\ref{sec:weak} we have shown the full satured weak automaton for both the specification and the implementation of the simple protocol.
@@
 
-The first piece of code is the textual definition of the SimpleProtSec
+The first piece of code is the textual definition of the SimpleProtSpec
 pNet, that was drawn in Figure \ref{SimpleProt:Impl}, page \pageref{SimpleProt:Impl}. This code should be intuitive enough to read, with the following
-conventions, that brings some user-friendly features that are maps by the editor into pure pNet constructs.
+conventions, that brings some user-friendly features that are mappeds by the editor into pure pNet constructs.
 
@@
     variables.
-  \item Variables can be declared either: inside a pLTS state (normal
-    state variable), as global variable of a pLTS (see e.g. ...), or
-    as an input variable in a transition, as \texttt{?msg} in pLTS M1
-    here.
-  \item the variables in the guards of synchronisation vectors do not need to be explicitely quantified: all variable in a guard that does not appear inside the vector actions will be recognised as bound by a \emph{foral} quantifier inside the guard.
-    \item the tools will check that everything is correctly declared, and that variables are used properly, that vectors have coherent length, etc.
+  \item Variables can be declared as global variables of a pLTS (e.g. \texttt{m\_msg} in \texttt{M1}), or a pNet Node in the case of synchronisation vector variables (e.g. \texttt{p\_a}),
+    or as input variables in a pLTS, as \texttt{?msg} in \texttt{M1}.
+  \item the variables in the guards of synchronisation vectors do not need to be explicitely quantified: all variables in a guard that do not appear inside the vector actions will be recognised as bound by a \emph{forall} quantifier inside the guard.
+    \item the tools will check that everything is correctly declared, and that variables are used properly and do not conflict between different objetcs, that vectors have coherent length, etc.
 \end{itemize}
@@
   root SimpleProtImpl2
-
 const in,out:Action
@@
   vars m_msg:Data m_ec:Int
-
 state m0
   transition m_recv(msg,c) -> m1 {m_msg:=msg, m_ec:=c}
-
 state m1
@@
   transition synchro($tau) -> m2
-
 state m2
@@
   vars  s_msg:Data s_ec:Int
-
 state s0
   transition s_recv(msg) -> s1 {s_msg:=msg, s_ec:=0}
-
 state s1
   transition s_send(s_msg, s_ec) -> s2 
-
 state s2
@@
   vars r_msg:Data r_ec:Int
-
 state r0
   transition r_recv(msg,c) -> r1 {r_msg:=msg, r_ec:=c}
-
 state r1
   transition r_send(r_msg, r_ec) -> r2
-
 state r2
@@
 
-It is based on the observation that states 202 and 000 are only linked by a "pure $\tau$" transition, and have exactly the same possible behaviours.
+This drawing is based on the observation that states 202 and 000 are only linked by a "pure $\tau$" transition, and have exactly the same possible behaviours.
 More tricky, they do not have the same state variables, as 202 has the variables of state $s2$, but none of these variables are used in transitions from 202.
-In this configuration we can guarantee that they are Weak bisimilar, and merge their (incoming and outgoing) transitions in the Figure. We denote this 
+In this configuration we can guarantee that they are Weak bisimilar, and we have merged their (incoming and outgoing) transitions in the Figure. We denote this 
 equivalence class of states as $\{000,202\}$.
@@
 
-All the following transitions are parametrized by an integer $n\in \mathcal{N}$, meaning they stand for the (infinite) set of weak OTs. 
-In some cases, this set is further restricted (see e.g. $WI_{7b}(n)$), in which case we have added an explicit quantifier.
+All the following transitions are parametrized by an integer $n\in \mathcal{N}$, meaning they stand for the corresponding (infinite) set of weak OTs. 
+In some cases, this set is further restricted (see e.g. $WI_{7b}(n)$), in which cases we have added an explicit quantifier.
 \smallskip
@@
 $ WI_4P(n) = \openrule
-         {\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], 
+         {\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], \\
    (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec}+n, \texttt{s\_ec}\gets \texttt{s\_ec}+n)}
@@
 $
+
 and
 $ WI_4Q(n) = \openrule
-         {\{\texttt{Q}\mapsto \texttt{q-b}\}, [\forall \texttt{m,ec}. \texttt{q-b} \neq \texttt{q-recv(m,ec)} ],
+         {\{\texttt{Q}\mapsto \texttt{q-b}\}, [\forall \texttt{m,ec}. \texttt{q-b} \neq \texttt{q-recv(m,ec)} ],\\
    (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec}+n, \texttt{s\_ec}\gets \texttt{s\_ec}+n)}
@@
 
-We will check here 2 of these conditions.
 Preliminary remarks:
@@
 
-  \medskip
-Let us start with the first pair: $SS_1 << WI_1$, where:
+  In our running example in page \pageref{subsubsection:runnig example}, we have shown the proof for one of the
+transitions of ($\text{b0},  202,  True$), namely that $SS_3$ is covered by $WI_3(0)$.
+We give here another example with $SS_1 << WI_1$, from the first triple ($\text{b0},  000,  True$). It includes less trivial predicates in the OTs:
 
@@
 
-\medskip That is trivialy true, choosing pa-2 = pa-1 for each p-a1.
+\medskip That is trivialy true, choosing \texttt{p-a1=p-a2} for each given \texttt{p-a1}.
 
@@
   \bigskip
-  All others pairs from this set are just as trivialy prove true.
+  All others pairs from this set are just as easily proved true.
 

### 2020-07-09 2016-Weak-FH-Bisim/WeakBisim.tex
corrections + RW

@@
 \author{Rab\'ea Ameur-Boulifa}
-                          % Activate to display a given date or no date
+\address{LTCI, T\'el\'ecom Paris, Institut Polytechnique de Paris, France
+}         
+\email{rabea.ameur-boulifa@telecom-paris.fr}                % Activate to display a given date or no date
 
@@
 There exist several equivalence relations for programs, and bisimulations are among the most versatile of these equivalences.
-Among bisimulation relations one distinguishes strong bisimulation, that requires that each action of a program is simulated by a single action of the equivalent program, an weak bisimulations that  is a coarser relations, allowing some of the actions to be
+Among bisimulation relations one distinguishes strong bisimulation, that requires that each action of a program is simulated by a single action of the equivalent program, a weak bisimulation that  is a coarser relations, allowing some of the actions to be
   invisible or internal moves, and thus not simulated by the equivalent program.
@@
 
-This article defines bisimulation relations for the pNet modelfor the comparison of systems specified as pNets.
+This article defines bisimulation relations for the pNet model for the comparison of systems specified as pNets.
  We first define a strong bisimulation for open pNets.
@@
       True, i.e. the states are related when the variables in $V_1$ and $V_2$ verify the 
-      predicate $\Pred_{s,t}$. By nature, this is well-defined if the variales of the two open automata are disjoint, i.e.  $V_1\cap V_2=\emptyset$.
+      predicate $\Pred_{s,t}$. By nature, this is well-defined if the variables of the two open automata are disjoint, i.e.  $V_1\cap V_2=\emptyset$.
  FH-bisimulation is defined formally: 
@@
 
-\begin{example} Figure \ref{WOT2} shows the construction of one of the weak transitions of the Specification OA.
+\begin{example} [A weak open-transition]
+Figure \ref{WOT2} shows the construction of one of the weak transitions of the Specification OA.
 On the top we show the subset of the original open automaton (from Figure \ref{SimpleProtCounter:SpecOA}) considered here, and at the bottom the generated weak transition.
@@
 
-  \begin{example}
+  \begin{example}[A weak open automaton]
     Figures \ref{SimpleProtCounter:WeakSpecOA} and \ref{SimpleProtCounter:ImplWOA2} respectively show the weak automata of the simple protocol specification and implementation.
@@
 
-We can now show some of the weak OTs of Figure \ref{SimpleProtCounter:ImplWOA2} (the full table is included in Appendix \ref{Appendix:FullExample}) :
+We can now show some of the weak OTs of Figure \ref{SimpleProtCounter:ImplWOA2} (the full table is included in Appendix \ref{Appendix:FullExample}).
 As we have seen above, the effect of rule $WT_3$ when a silent action have an effect on the variable $ec$ will generate an infinite family of WOTs, depending on the number of iterations through the loops.
@@
       condition: the only vectors having $\tau$ as an action of a
-      sub-net are of the form ``$< -, \tau, -> -> \tau$''.
-    \item We must take care of variable name conflicts: in our example, the variables of the 2 systems already have different names, but the action parameters occurring in the transitions (m, msg, ec) are the same, that is not correct.
+      sub-net are of the form ``$< -, \tau, -> \rightarrow \tau$''.
+    \item We must take care of variable name conflicts: in our example, the variables of the 2 systems already have different names, but the action parameters occurring in the transitions (\texttt{m}, \texttt{msg}, \texttt{ec}) are the same, that is not correct.
 In the tools, this is managed by the static semantic layer; in the following example, we have renamed all conflicting variables with 1 for the Spec, and 2 for the Impl.
@@
   Checking that $\mathcal{R}$ is a weak FH-Bisimulation means checking, for each of these triples, that each (strong) OT of one the states corresponds to a set of WOTs of the other, using the conditions from Definition \ref{def-Weak-bisim}.
-  We give here one  example: consider the second triple from the table, and transition $SS_3$ from state $b0$. Its easy to guess that it will correspond to $WI_3(0)$ of state $202$.
+  We give here one  example: consider the second triple from the table, and transition $SS_3$ from state \texttt{b0}. Its easy to guess that it will correspond to $WI_3(0)$ of state $202$.
 
@@
 
-\medskip That reduces to:
+\medskip That is reduced to:
 
@@
 In
+
 \cite{Johnson:2013:CBSE,Johnson:2014:qosa}, the authors investigate several methodologies for the compositional verification of software systems, with the aim to verify reconfigurable component systems.
@@
 
+\TODO{Methodologies for reasoning about abstract semantics of open systems can be found in \cite{BaldanBB:07,BuscemiM:08,Dubut:20}, authors introduce  behavioural equivalences for open systems from various symbolic approaches.
+Working in the setting of process calculi, some close relations  exist with the work  of the authors of \cite{BaldanBB:07}, where both approaches are based
+on some kinds of labelled transition systems.
+The distinguishing feature of their approach is the transitions systems are labelled with logical  formulae that provides  an abstract characterisation of the structure that a hole must possess and of the actions it can perform in order to allow a transition to fire.}
+
 \ERIC{J'ai copie/colle ici le Related Work que Zechen a mis dans notre
@@
 Wimmer et al. present a signature-based approach to compute Bisimulation, implemented by using BDDs\cite{wimmer2006sigref}.
-Lin present a symbolic bisimulation between symbolic transition graph with assignments(STGA), as mentioned in \emph{Introduction}, bring us lots of inspirations.
+Lin present a symbolic bisimulation between symbolic transition graph with assignments (STGA), as mentioned in \emph{Introduction}, bring us lots of inspirations.
 
@@
 skeletons, or distributed algorithms.
-We have developped tool support for computing the
+We have developed tool support for computing the
 symbolic semantics in term of open-automata \cite{QBMZ-AVOCS18}, and have
@@
        	More precisely,  $t_{px} \in ({t'_p})^{p\in P'}$ where $({t'_p})^{p\in 
-       		P'}$\hl{$P'\subseteq P$} \TODO{NO : there is no relation between the two sets: they are not comparable} is 
+       		P'}$ and $P'\subseteq P$  is 
        	the set of states relating ${s}'$ and $u_{pxy}$ (the states used in the open transition must belong to the set of states ensuring the transitive relation).
@@
 \alpha_k\displaystyle{\subst{\!\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}}\]
-\hl{With}~\ref{eqproofbeta}, we now have. Recall that the actions $\alpha_k$ are the actions $\alpha'_{p}$ that are observable: 
+From equation~\ref{eqproofbeta}, we obtain the following equation (we recall that the actions $\alpha_k$ are the actions $\alpha'_{p}$ that are observable): 
 \begin{eqnarray*}
@@
 pNet, that was drawn in Figure \ref{SimpleProt:Impl}, page \pageref{SimpleProt:Impl}. This code should be intuitive enough to read, with the following
-conventions, that brings some user-friendly features that are mappeds by the editor into pure pNet constructs.
+conventions, that brings some user-friendly features that are mapped by the editor into pure pNet constructs.
 
@@
     typically \texttt{in(msg)}, or constants without argument, denoted
-    as \texttt{\$tau}. Identifiers without the ``?'' marker are
+    as \texttt{\$tau}. Identifiers without the ``\$'' marker are
     variables.
@@
     or as input variables in a pLTS, as \texttt{?msg} in \texttt{M1}.
-  \item the variables in the guards of synchronisation vectors do not need to be explicitely quantified: all variables in a guard that do not appear inside the vector actions will be recognised as bound by a \emph{forall} quantifier inside the guard.
-    \item the tools will check that everything is correctly declared, and that variables are used properly and do not conflict between different objetcs, that vectors have coherent length, etc.
+  \item The variables in the guards of synchronisation vectors do not need to be explicitly quantified: all variables in a guard that do not appear inside the vector actions will be recognised as bound by a \emph{forall} quantifier inside the guard.
+    \item The tools will check that everything is correctly declared, and that variables are used properly and do not conflict between different objects, that vectors have coherent length, etc.
 \end{itemize}
-
+\bigskip
 %\TODO{Je ne peux pas refaire tourner le code, il faut que je modifie le pNet Editor pour qu'ils n'utilise plus les variables d'etat... Donc les 3 prochaines pages sont obsoletes...}
@@
 
+\bigskip
 The corresponding generated Open Automaton was given in Figure \ref{SimpleProtCounter:SpecOA},
-page \pageref{SimpleProtCounter:SpecOA}.
+page \pageref{SimpleProtCounter:SpecOA}.\\
 
 Next is the code for the SimpleProtImpl pNet:
-
+\medskip
 \begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
@@
 
-\medskip That is trivialy true, choosing \texttt{p-a1=p-a2} for each given \texttt{p-a1}.
+\medskip That is trivially true, choosing \texttt{p-a1=p-a2} for each given \texttt{p-a1}.
 

### 2020-07-10 2016-Weak-FH-Bisim/WeakBisim.tex
Reorganise la section related-work

@@
 
-\TODO{retravailler le paragraphe ci dessous}
+To the best of our knowledge, there is no other research works on the Bisimulation Equivalence between such complicate(open, symbolic, parameterised, with loops and assignments) system models, with providing fully complete algorithms.
+For the sake of completeness, we give a brief overview of other Open and/or Symbolic Bisimulation researches.
+
+\TODO{Logique de reorganisation: 1: Open et compositionel [15,13, peut-etre 17], 2: symbolic et data-sensitive [lin, rathke 4 et ?, 5, puis Lotos 18, Pi-calc 16,19,20,22, quantum 25.]}
+
+\paragraph{Open and Compositional systems}
+
+\TODO{retravailler le paragraphe ci dessous: faire ref a Facs-2013 (reconfig ds pNets) - virer 14 (probabilistic) ?}
 In
-
 \cite{Johnson:2013:CBSE,Johnson:2014:qosa}, the authors investigate several methodologies for the compositional verification of software systems, with the aim to verify reconfigurable component systems.
@@
 
-\TODO{Methodologies for reasoning about abstract semantics of open systems can be found in \cite{BaldanBB:07,BuscemiM:08,Dubut:20}, authors introduce  behavioural equivalences for open systems from various symbolic approaches.
+\TODO{Et ou on place celui-la: 
+https://www.researchgate.net/publication/322674459\_Bisimulations\_on\_Data\_Graphs ?
+}
+
+\TODO{Methodologies for reasoning about abstract semantics of open systems can be found in \cite{BaldanBB:07,Dubut:20} --verifier Dubut--, authors introduce  behavioural equivalences for open systems from various symbolic approaches.
 Working in the setting of process calculi, some close relations  exist with the work  of the authors of \cite{BaldanBB:07}, where both approaches are based
@@
 
-\ERIC{J'ai copie/colle ici le Related Work que Zechen a mis dans notre
-  papier bisim...
-  Pas tres satisfaisant pour les aspects Weak, mais quelques inputs a
-  regarder}
-
-To the best of our knowledge, there is no other research works on the Bisimulation Equivalence between such complicate(open, symbolic, parameterised, with loops and assignments) system models, with providing fully complete algorithms.
-For the sake of completeness, we give a brief overview of other Symbolic Bisimulation researches.
-
-One line of research is providing Symbolic Bisimulation for different model or language. 
-In Calder's work\cite{calder2001symbolic}, they define a symbolic semantic for full LOTOS, with a symbolic bisimulation over it;
-Borgstrom et al., Delaune et al.
+\paragraph{Symbolic and data-sensitive systems}
+
+Lin present a symbolic bisimulation between symbolic transition graph with assignments (STGA), as mentioned in \emph{Introduction}, bring us lots of inspirations.
+
+Research related to the keyword "Symbolic Bisimulation" refer to two very different domains, namely BDD-like techniques for modeling and computing finite-state bisimulations, that are not related to our topic; and symbolic semantics for data-dependant or high-order systems, that are very close in spirit to our approach.
+In this last area, we can mention
+Calder's work \cite{calder2001symbolic}, that  defines a symbolic semantic for full LOTOS, with a symbolic bisimulation over it;
+Borgstrom et al., Liu et al, Delaune et al.
 and Buscemi et al.
-provide symbolic semantic and equivalence for different variants of pi calculus respectively\cite{borgstrom2004symbolic}\cite{delaune2007symbolic}\cite{buscemi2008open}, and later in 2012 Liu's work provided symbolic bisimulation  for full applied pi calculus\cite{liu2010complete};
-The most recent work, Feng et al. provide a symbolic bisimulation for quantum processes
-\cite{feng2014symbolic}.
-All the above works, didn't give a complete approach for verification, and the models on which these works based are simpler or different than ours.
-
-Another line of research is devising the algorithm for computing symbolic Bisimulation Equivalence.
-In Dovier's work, they provide a rank-based algorithm, layering the input model to compute bisimulation\cite{dovier2002rank}. 
-Baldan et al. also focus on open systems, using a logical programming language \emph{Prolog} to model the systems and compute Bisimulation\cite{baldan2001compositional}.
-Wimmer et al. present a signature-based approach to compute Bisimulation, implemented by using BDDs\cite{wimmer2006sigref}.
-Lin present a symbolic bisimulation between symbolic transition graph with assignments (STGA), as mentioned in \emph{Introduction}, bring us lots of inspirations.
+providing symbolic semantic and equivalence for different variants of pi calculus respectively \cite{borgstrom2004symbolic,delaune2007symbolic,liu2010complete,buscemi2008open}; and more recently
+ Feng et al. provide a symbolic bisimulation for quantum processes \cite{feng2014symbolic}.
+All the above works, didn't give a complete approach for verification, and the models on which these works based are definitely different from ours.
+
+% Another line of research is devising the algorithm for computing symbolic Bisimulation Equivalence.
+% In Dovier's work, they provide a rank-based algorithm, layering the input model to compute bisimulation\cite{dovier2002rank}. 
+% Baldan et al. also focus on open systems, using a logical programming language \emph{Prolog} to model the systems and compute Bisimulation\cite{baldan2001compositional}.
+%Wimmer et al. present a signature-based approach to compute Bisimulation, implemented by using BDDs\cite{wimmer2006sigref}.
 

### 2020-07-14 2016-Weak-FH-Bisim/WeakBisim.tex
related work

@@
 
-\paragraph{Open and Compositional systems}
-
-\TODO{retravailler le paragraphe ci dessous: faire ref a Facs-2013 (reconfig ds pNets) - virer 14 (probabilistic) ?}
+\subsubsection*{Open and Compositional systems}
+\TODO{retravailler le paragraphe ci dessous: faire ref a Facs-2013 (reconfig ds pNets) - virer 14 (probabilistic) ?} \cite{GasparHM:2013}
 In
@@
 
-\paragraph{Symbolic and data-sensitive systems}
-
-Lin present a symbolic bisimulation between symbolic transition graph with assignments (STGA), as mentioned in \emph{Introduction}, bring us lots of inspirations.
+\subsubsection*{Symbolic and data-sensitive systems}
+In \cite{Abriola:2018} the authors present the notion of ''data-aware'' bisimulations on data graphs, computation of such bisimulations is 
+studied based on XPath logical language extended with tests for data equality.
+As mentioned in the \emph{Introduction}, the work that brought us a lot of inspirations are those of Lin et al.
+\cite{HENNESSY:95, Lin:96}.
+They developed the theory of symbolic transition graphs (STG), and the associated symbolic (early and late) bisimulations, they also study STGs with assignments which can be a model for message-passing processes.
+
+%Lin present a symbolic bisimulation between symbolic transition graph with assignments (STGA), as mentioned in \emph{Introduction}, bring us lots of inspirations.
 
@@
 Naturally we are now working toward an implementation of weak FH-Bisimulation. 
-The challenges here, in the context of uour symbolic systems, is not so much algorithmic complexity,
+The challenges here, in the context of our symbolic systems, is not so much algorithmic complexity,
 as was the case with classical weak bisimulation on finite models, but decidability and termination.
-Two main directions should be explored, either with an explicite construction of the weak transition, but this step in
+Two main directions should be explored, either with an explicit construction of the weak transition, but this step in
 itself may introduce non-termination, or a direct implementation of the weak bisimulation definition, without
@@
 \end{multline*}
-The three for all statements (on $J_a$, $J_b$, and $J_c$) can be concatenated using $\dotcup$, the list union lifted to indexed sets (if $\gamma=\gamma'$ and $\gamma''=\gamma'''$ then $\gamma\dotcup\gamma''=\gamma'\dotcup\gamma'''$).
+The three for all statements (on $J_a$, $J_b$ and $J_c$) can be concatenated using $\dotcup$, the list union lifted to indexed sets (if $\gamma=\gamma'$ and $\gamma''=\gamma'''$ then $\gamma\dotcup\gamma''=\gamma'\dotcup\gamma'''$).
 \begin{multline*}\forall j\in J_a\uplus J_b\uplus J_c.

### 2020-07-15 2016-Weak-FH-Bisim/WeakBisim.tex
deux paragraph reecrits (en bleu)

@@
 
-To the best of our knowledge, there is no other research works on the Bisimulation Equivalence between such complicate(open, symbolic, parameterised, with loops and assignments) system models, with providing fully complete algorithms.
-For the sake of completeness, we give a brief overview of other Open and/or Symbolic Bisimulation researches.
+\ERIC{ To the best of our knowledge, there is no other research works on Weak Bisimulation Equivalences between such complicate system models (open, symbolic, parameterised, with loops and assignments)
+For the sake of completeness, we give a brief overview of other Open and/or Symbolic Bisimulation researches, event though these are not specific to "weak" approaches.}
 
@@
 are quite different from ours, in particular they are much less structured, and translating them is clearly outside the scope of this article.
-Additionally, the more compositional constraint resolution provided by the authors could also be interesting to make our SMT proofs scale better (inside a single pNet for example), the integration of the Z3 framework described in \cite{Johnson:2014:qosa} with our proof theory for open pNets would also be worth investigating from a practical point of view.
-One major different however is that pNets in their current state are not much adapted to probabilistic verification contrarily to \cite{Johnson:2014:qosa} but they are better suited to verify complex behavioural properties.
-
-\TODO{Et ou on place celui-la: 
-https://www.researchgate.net/publication/322674459\_Bisimulations\_on\_Data\_Graphs ?
-}
-
-\TODO{Methodologies for reasoning about abstract semantics of open systems can be found in \cite{BaldanBB:07,Dubut:20} --verifier Dubut--, authors introduce  behavioural equivalences for open systems from various symbolic approaches.
+%Additionally, the more compositional constraint resolution provided by the authors could also be interesting to make our SMT proofs scale better (inside a single pNet for example), the integration of the Z3 framework described in \cite{Johnson:2014:qosa} with our proof theory for open pNets would also be worth investigating from a practical point of view.
+%One major different however is that pNets in their current state are not much adapted to probabilistic verification contrarily to \cite{Johnson:2014:qosa} but they are better suited to verify complex behavioural properties.
+
+%\TODO{Et ou on place celui-la:  https://www.researchgate.net/publication/322674459\_Bisimulations\_on\_Data\_Graphs ? }
+
+Methodologies for reasoning about abstract semantics of open systems can be found in \cite{BaldanBB:07,Dubut:20} --verifier Dubut--, authors introduce  behavioural equivalences for open systems from various symbolic approaches.
 Working in the setting of process calculi, some close relations  exist with the work  of the authors of \cite{BaldanBB:07}, where both approaches are based
 on some kinds of labelled transition systems.
-The distinguishing feature of their approach is the transitions systems are labelled with logical  formulae that provides  an abstract characterisation of the structure that a hole must possess and of the actions it can perform in order to allow a transition to fire.}
+The distinguishing feature of their approach is the transitions systems are labelled with logical  formulae that provides  an abstract characterisation of the structure that a hole must possess and of the actions it can perform in order to allow a transition to fire.
 
 \subsubsection*{Symbolic and data-sensitive systems}
-In \cite{Abriola:2018} the authors present the notion of ''data-aware'' bisimulations on data graphs, computation of such bisimulations is 
-studied based on XPath logical language extended with tests for data equality.
-As mentioned in the \emph{Introduction}, the work that brought us a lot of inspirations are those of Lin et al.
+\ERIC{ As mentioned in the \emph{Introduction}, the work that brought us a lot of inspirations are those of Lin et al.
 \cite{HENNESSY:95, Lin:96}.
 They developed the theory of symbolic transition graphs (STG), and the associated symbolic (early and late) bisimulations, they also study STGs with assignments which can be a model for message-passing processes.
+Our work extends these in several ways: first our models are compositional, and our bismulations come with effective conditions for being preserved by pNet composition (ie congruent), even for the weak version.
+Then our settings for management of data types are much less restrictive, thanks to the satisfiability engines, while Lin's work was limited to data-independant systems.
+}
+
+In a similar way, \cite{Abriola:2018} presents a notion of ''data-aware'' bisimulations on data graphs, in which computation of such bisimulations is studied based on XPath logical language extended with tests for data equality.
 

### 2020-07-15 2016-Weak-FH-Bisim/WeakBisim.tex
small typos in appendix

@@
 $\forall \texttt{p-a1}. \{True \land \forall \texttt{m1}. \texttt{p-a1} \neq \texttt{p-send(m1)}\\
- \hspace{3mm} \implies \exists \texttt{pa-2}. 
+ \hspace{3mm} \implies \exists \texttt{p-a2}. 
 (\texttt{p-a1} = \texttt{p-a2}
@@
 
-\medskip That is trivially true, choosing \texttt{p-a1=p-a2} for each given \texttt{p-a1}.
+\medskip That is trivially true, choosing \texttt{p-a2=p-a1} for each given \texttt{p-a1}.
 
@@
   \bigskip
-  All others pairs from this set are just as easily proved true.
+  All others pairs from this set are just as easily proven true.
 

### 2020-07-15 2016-Weak-FH-Bisim/WeakBisim.tex
ajout de ref

@@
 
-\ERIC{ To the best of our knowledge, there is no other research works on Weak Bisimulation Equivalences between such complicate system models (open, symbolic, parameterised, with loops and assignments)
+\ERIC{ To the best of our knowledge, there is no other research works on Weak Bisimulation Equivalences between such complicate system models (open, symbolic, parameterised, with loops and assignments).
 For the sake of completeness, we give a brief overview of other Open and/or Symbolic Bisimulation researches, event though these are not specific to "weak" approaches.}
@@
 
-Methodologies for reasoning about abstract semantics of open systems can be found in \cite{BaldanBB:07,Dubut:20} --verifier Dubut--, authors introduce  behavioural equivalences for open systems from various symbolic approaches.
-Working in the setting of process calculi, some close relations  exist with the work  of the authors of \cite{BaldanBB:07}, where both approaches are based
+Methodologies for reasoning about abstract semantics of open systems can be found in \cite{BaldanBB:2002, BaldanBB:07,Dubut:20}, authors introduce  behavioural equivalences for open systems from various symbolic approaches.
+Working in the setting of process calculi, some close relations  exist with the work  of the authors of \cite{BaldanBB:2002,BaldanBB:07}, where both approaches are based
 on some kinds of labelled transition systems.
 The distinguishing feature of their approach is the transitions systems are labelled with logical  formulae that provides  an abstract characterisation of the structure that a hole must possess and of the actions it can perform in order to allow a transition to fire.
+\TODO{Logical formulae are suitable formats that  capture the general class of components that can take part in placeholders of the system during its evolution.}
 
@@
 \ERIC{ As mentioned in the \emph{Introduction}, the work that brought us a lot of inspirations are those of Lin et al.
-\cite{HENNESSY:95, Lin:96}.
+\cite{HENNESSY:95, Lin:96, IngolfsdottirL:2001}.
 They developed the theory of symbolic transition graphs (STG), and the associated symbolic (early and late) bisimulations, they also study STGs with assignments which can be a model for message-passing processes.
-Our work extends these in several ways: first our models are compositional, and our bismulations come with effective conditions for being preserved by pNet composition (ie congruent), even for the weak version.
-Then our settings for management of data types are much less restrictive, thanks to the satisfiability engines, while Lin's work was limited to data-independant systems.
+Our work extends these in several ways: first our models are compositional, and our bismulations come with effective conditions for being preserved by pNet composition (i.e.
+congruent), even for the weak version.
+Then our settings for management of data types are much less restrictive, thanks to the satisfiability engines, while Lin's work was limited to data-independent systems.
 }
@@
 
-Open pNets are pNets with holes; they are adapted to represent processes parameterised by the behaivour of other processes, like composition operators or interaction 
+Open pNets are pNets with holes; they are adapted to represent processes parameterised by the behaviour of other processes, like composition operators or interaction 
 protocols that synchronize the actions of processes that can be plugged afterwards. Open

### 2020-07-16 2016-Weak-FH-Bisim/WeakBisim.tex
Added comments on [Ingolfsdottir] in Intro

@@
 developed a symbolic behavioural semantics, and proved algebraic properties.
+In \cite{IngolfsdottirL:2001}, Lin and Ingolfsdottir developped a full hierarchy of
+bisimulation equivalences, together with a proof system, for value passing CCS,
+including notions of symbolic behavioral semantics and various symbolic 
+bisimulations (early and late, strong and weak, and their congruent versions).
 Separately J. Rathke~\cite{HennessyRathke:TCS98} defined another
@@
 
-This article provides a theoretical background that allows us to implement such a verification platform.
-We build upon the concept of pNets that allowed us to give a behavioural semantics of distributed components and verify the correctness of distributed applications in the past 15 years.
-pNets  is a
+This article provides a theoretical background that allows us to implement such a verification 
+platform. We build upon the concept of pNets that allowed us to give a behavioural semantics 
+of distributed components and verify the correctness of distributed applications in the past 15 years. pNets  is a
 low level semantic framework for expressing the behaviour of various
@@
 The distinguishing feature of their approach is the transitions systems are labelled with logical formulae that provides  an abstract characterisation of the structure that a hole must possess and of the actions it can perform in order to allow a transition to fire.
-\TODO{Logical formulae are suitable formats that  capture the general class of components that can take part in placeholders of the system during its evolution.}
+\TODO{Logical formulae are suitable formats that capture the general class of components that can take part in a synchronisation between the placeholders of the system during its evolution.}
 
@@
 \cite{HENNESSY:95, Lin:96, IngolfsdottirL:2001}.
-They developed the theory of symbolic transition graphs (STG), and the associated symbolic (early and late) bisimulations, they also study STGs with assignments which can be a model for message-passing processes.
+They developed the theory of symbolic transition graphs (STG), and the associated symbolic (early and late, strong and weak) bisimulations, they also study STGs with assignments as a model for message-passing processes.
 Our work extends these in several ways: first our models are compositional, and our bismulations come with effective conditions for being preserved by pNet composition (i.e.
 congruent), even for the weak version.
+This result is more general than the bisimulation congruences for value-passing CCS in \cite{IngolfsdottirL:2001}.
 Then our settings for management of data types are much less restrictive, thanks to the satisfiability engines, while Lin's work was limited to data-independent systems.

### 2020-07-18 2016-Weak-FH-Bisim/WeakBisim.tex
Derniere (??) edition de related work...

@@
 various symbolic encodings of the
-transitions~\cite{deSimone85,Larsen87,HennessyLin:TCS95,Linconcur96}. 
-In \cite{Linconcur96}, H.M. Lin addressed value-passing calculi, for which he
-developed a symbolic behavioural semantics, and proved algebraic properties.
-In \cite{IngolfsdottirL:2001}, Lin and Ingolfsdottir developped a full hierarchy of
+transitions~\cite{deSimone85,Larsen87}. 
+In \cite{IngolfsdottirL:2001,HennessyLin:TCS95}, Lin, Ingolfsdottir and Hennessy developped a full hierarchy of
 bisimulation equivalences, together with a proof system, for value passing CCS,
 including notions of symbolic behavioral semantics and various symbolic 
-bisimulations (early and late, strong and weak, and their congruent versions).
-Separately J. Rathke~\cite{HennessyRathke:TCS98} defined another
-symbolic semantics for 
+bisimulations (early and late, strong and weak, and their congruent versions). They also extended this work to models with explicit assignements \cite{Linconcur96}.
+Separately J. Rathke~\cite{HennessyRathke:TCS98} defined another symbolic semantics for 
 a parameterised broadcast calculus, together with strong and weak bisimulation
@@
 
-\ERIC{ To the best of our knowledge, there is no other research works on Weak Bisimulation Equivalences between such complicate system models (open, symbolic, parameterised, with loops and assignments).
-For the sake of completeness, we give a brief overview of other Open and/or Symbolic Bisimulation researches, event though these are not specific to "weak" approaches.}
-
-\TODO{Logique de reorganisation: 1: Open et compositionel [15,13, peut-etre 17], 2: symbolic et data-sensitive [lin, rathke 4 et ?, 5, puis Lotos 18, Pi-calc 16,19,20,22, quantum 25.]}
+\ERIC{ To the best of our knowledge, there are not many research works on Weak Bisimulation Equivalences between such complicate system models (open, symbolic, data-aware, with loops and assignments).
+We give a brief overview of other related publications, focussing first on Open and Compositional approaches, then on Symbolic Bisimulation for data-sensitive systems.}
+
+%\TODO{Logique de reorganisation: 1: Open et compositionel [15,13, peut-etre 17], 2: symbolic et data-sensitive [lin, rathke 4 et ?, 5, puis Lotos 18, Pi-calc 16,19,20,22, quantum 25.]}
 
 \subsubsection*{Open and Compositional systems}
-\TODO{retravailler le paragraphe ci dessous: faire ref a Facs-2013 (reconfig ds pNets) - virer 14 (probabilistic) ?} \cite{GasparHM:2013}
-In
+%\TODO{retravailler le paragraphe ci dessous: faire ref a Facs-2013 (reconfig ds pNets) - virer 14 (probabilistic) ?} \cite{GasparHM:2013}
+\ERIC{In
 \cite{Johnson:2013:CBSE,Johnson:2014:qosa}, the authors investigate several methodologies for the compositional verification of software systems, with the aim to verify reconfigurable component systems.
@@
 These works clearly highlight the interest of incremental and compositional verification in a very general setting.
-By adding more structure to the composition model and designing a dedicated bisimulation theory, we show here how to enforce a compositional proof system that is more powerful than independent sets of variables.
+In our own work on open pNets, adding more structure to the composition model, we show how to enforce a compositional proof system that is more powerful than independent sets of variables.
 Our theory has also been encoded into an SMT solver and it would be interesting to investigate how the examples of evolving systems studied by the authors could be encoded into pNet and verified by our framework.
@@
 are quite different from ours, in particular they are much less structured, and translating them is clearly outside the scope of this article.
+In previous work \cite{gaspar:hal-00916115}, we also have shown how (closed) pNet models could be used to encode and verify finite instances of reconfigurable component systems. }
 %Additionally, the more compositional constraint resolution provided by the authors could also be interesting to make our SMT proofs scale better (inside a single pNet for example), the integration of the Z3 framework described in \cite{Johnson:2014:qosa} with our proof theory for open pNets would also be worth investigating from a practical point of view.
@@
 The distinguishing feature of their approach is the transitions systems are labelled with logical formulae that provides  an abstract characterisation of the structure that a hole must possess and of the actions it can perform in order to allow a transition to fire.
-\TODO{Logical formulae are suitable formats that capture the general class of components that can take part in a synchronisation between the placeholders of the system during its evolution.}
+Logical formulae are suitable formats that capture the general class of components that can act as the placeholders of the system during its evolution.
 
@@
 \ERIC{ As mentioned in the \emph{Introduction}, the work that brought us a lot of inspirations are those of Lin et al.
-\cite{HENNESSY:95, Lin:96, IngolfsdottirL:2001}.
+\cite{IngolfsdottirL:2001,HennessyLin:TCS95,Linconcur96}.
 They developed the theory of symbolic transition graphs (STG), and the associated symbolic (early and late, strong and weak) bisimulations, they also study STGs with assignments as a model for message-passing processes.
@@
 This result is more general than the bisimulation congruences for value-passing CCS in \cite{IngolfsdottirL:2001}.
-Then our settings for management of data types are much less restrictive, thanks to the satisfiability engines, while Lin's work was limited to data-independent systems.
+Then our settings for management of data types are much less restrictive, thanks to our use of satisfiability engines, while Lin's algorithms were limited to data-independent systems.
 }
@@
 
-We are currently extending this work,  looking at  both further properties of 
-FH-bisimulation, but also
-the relations with existing equivalences on closed systems.
+We are currently extending this work,  looking at  both further properties of FH-bisimulation, but also
+the relations with existing equivalences on both closed and open systems. \ERIC{In particular, our model being significantly different from those considered in \cite{IngolfsdottirL:2001}, it
+would be interesting to compare our "FH" family of bisimulations with the hierarchy of symbolic bisimulations from these authors.}
 We also plan to apply open pNets to the study of complex composition

### 2020-07-19 2016-Weak-FH-Bisim/WeakBisim.tex
qques typos

@@
 transitions~\cite{deSimone85,Larsen87}. 
-In \cite{IngolfsdottirL:2001,HennessyLin:TCS95}, Lin, Ingolfsdottir and Hennessy developped a full hierarchy of
+In \cite{IngolfsdottirL:2001,HennessyLin:TCS95}, Lin, Ingolfsdottir and Hennessy developed a full hierarchy of
 bisimulation equivalences, together with a proof system, for value passing CCS,
-including notions of symbolic behavioral semantics and various symbolic 
-bisimulations (early and late, strong and weak, and their congruent versions). They also extended this work to models with explicit assignements \cite{Linconcur96}.
+including notions of symbolic behavioural semantics and various symbolic 
+bisimulations (early and late, strong and weak, and their congruent versions). They also extended this work to models with explicit assignments \cite{Linconcur96}.
 Separately J. Rathke~\cite{HennessyRathke:TCS98} defined another symbolic semantics for 
@@
 
-Research related to the keyword "Symbolic Bisimulation" refer to two very different domains, namely BDD-like techniques for modeling and computing finite-state bisimulations, that are not related to our topic; and symbolic semantics for data-dependant or high-order systems, that are very close in spirit to our approach.
+Research related to the keyword "Symbolic Bisimulation" refer to two very different domains, namely BDD-like techniques for modelling and computing finite-state bisimulations, that are not related to our topic; and symbolic semantics for data-dependant or high-order systems, that are very close in spirit to our approach.
 In this last area, we can mention
@@
 
-The right part of the disjunction, i.e.,
+The right part of the disjunction, i.e.
 \begin{mathpar}
@@
 \begin{enumerate}
-\item For the first $\tau$ OTs, i.e, $p\in [0\,..\,m_1]$. We have: \\
+\item For the first $\tau$ OTs, i.e. $p\in [0\,..\,m_1]$. We have: \\
 Either there is $i$ such that $p=n_i$, and thus $\beta_i$ and $\beta_{1 p j_0}$ are defined. In this case by Lemma~\ref{lem-Weakcompose1},  we have: 
@@
 
-\item For the last $\tau$ OTs, i.e, $p\in [0\,..\,m_2]$. We have similarly to the first case:\\
+\item For the last $\tau$ OTs, i.e. $p\in [0\,..\,m_2]$. We have similarly to the first case:\\
  Either there is $i$ such that $p=n'_i$, and thus $\beta_i$ and $\beta_{1 p j_0}$ are defined. In this case by Lemma~\ref{lem-Weakcompose1}, we have: 

### 2020-07-20 2016-Weak-FH-Bisim/WeakBisim.tex
petite relecture intro

@@
 
-This article defines bisimulation relations for the pNet model for the comparison of systems specified as pNets.
+This article defines bisimulation relations  for the comparison of systems specified as pNets.
  We first define a strong bisimulation for open pNets.
@@
 The main interest of our symbolic approach is to define a method to
-prove properties directly on open structures, that will be preserved
+prove properties directly on open structures; these properties will then be preserved
 by any correct instantiation of the holes.

### 2020-07-20 2016-Weak-FH-Bisim/WeakBisim.tex
petite passe sur RW and conclusion

@@
 nature of the model and the properties of compositionability of the
-equivalence relations thus play a major role here and are the main
-strengths of  our contribution.
+equivalence relations are thus  the main
+strengths of  our approach.
 
@@
 It relies on the definition of weak open transitions that are derived from transitions of the open automaton by concatenating invisible action transitions with one (visible or not) action transition.
-The precise definition of the concatenation is also a major contribution of this article.
+The precise and sound definition of the concatenation is also a major contribution of this article.
 \item A resulting weak bisimulation equivalence for open pNets and a simple static condition on synchronisation vectors inside pNets that is sufficient to ensure that weak bisimulation is compositional.
@@
 Logical formulae are suitable formats that capture the general class of components that can act as the placeholders of the system during its evolution.
+In our approach we purposely leave the algebra of action terms undefined but the only operation we allow on action of holes is the comparison with other actions.
+Defining properly the interaction between a logical formulae in the action and the logics of the pNet composition seems very difficult.
 
@@
 This article defines a strong and a weak bisimulation principles that are adapted to parameterised systems and hierarchical composition.
-Our bisimulation principle handles pNets parameters in the sense that two states might be or not in relation depending on the value of parameters.
+Our bisimulation principle handles pNet parameters in the sense that two states might be or not in relation depending on the value of parameters.
 Our strong  bisimulation is compositional by nature in the sense that bisimulation is maintained when composing processes.

### 2020-07-21 2016-Weak-FH-Bisim/WeakBisimSUBMITTED.tex
submitted version

--- 2020-07-20 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 }
+\author{Rab\'ea Ameur-Boulifa}
+\address{LTCI, T\'el\'ecom Paris, Institut Polytechnique de Paris, France
+}         
+\email{rabea.ameur-boulifa@telecom-paris.fr}
+
 \author{Ludovic Henrio}
@@
 %\date{}                                           % Activate to display a given date or no date
-\author{Rab\'ea Ameur-Boulifa}
-\address{LTCI, T\'el\'ecom Paris, Institut Polytechnique de Paris, France
-}         
-\email{rabea.ameur-boulifa@telecom-paris.fr}                % Activate to display a given date or no date
+               % Activate to display a given date or no date
 
@@
 
-Establishing equivalences between programs or system is crucial both for verifying correctness of programs, by establishing that two implementations are equivalent, and for justifying optimisations and program transformations, by establishing that a modified program is equivalent to the source one.
-There exist several equivalence relations for programs, and bisimulations are among the most versatile of these equivalences.
-Among bisimulation relations one distinguishes strong bisimulation, that requires that each action of a program is simulated by a single action of the equivalent program, a weak bisimulation that  is a coarser relations, allowing some of the actions to be
-  invisible or internal moves, and thus not simulated by the equivalent program.
-
-pNets is a generalisation of automata that includes parameters, and hierarchical composition.
-Open pNets are pNets with holes, i.e.
-placeholders inside the hierarchical structure  that can be filled by sub-systems.
-Reasoning on open pNets allows us to reason on open systems.
-  Open pNets have a notion of \emph{synchronised actions}
-  generalizing the usual internal actions (e.g. $\tau$ of CCS, or $i$
-  in Lotos).
-
-This article defines bisimulation relations  for the comparison of systems specified as pNets.
- We first define a strong bisimulation for open pNets.
-  In practice, as happens in process algebras, strong bisimulation is too strong, and
-  we need to define some coarser relations, taking into account
-  invisible or internal moves.
-  We then define an equivalence relation similar to
-  the classical \emph{weak bisimulation}, and study its properties.
-Among these properties we are interested in compositionality: If two systems are proven equivalent they will be undistinguishable by their context, and they will also be undistinguishable when their holes are filled with equivalent systems.
+Establishing equivalences between programs or system is crucial both for verifying
+correctness of programs, by establishing that two implementations are equivalent, and
+for justifying optimisations and program transformations, by establishing that a
+modified program is equivalent to the source one. There exist several equivalence
+relations for programs, and bisimulations are among the most versatile of these
+equivalences. Among bisimulation relations one distinguishes strong bisimulation, that
+requires that each action of a program is simulated by a single action of the equivalent
+program, a weak bisimulation that  is a coarser relations, allowing some of the actions
+to be invisible or internal moves, and thus not simulated by the equivalent program.
+
+pNets is a generalisation of automata that includes parameters, and hierarchical
+composition. Open pNets are pNets with holes, i.e. placeholders inside the hierarchical
+structure  that can be filled by sub-systems. Reasoning on open pNets allows us to
+reason on open systems. Open pNets have a notion of \emph{synchronised actions}
+generalizing the usual internal actions (e.g. $\tau$ of CCS, or $i$ in Lotos).
+
+This article defines bisimulation relations  for the comparison of systems specified as
+pNets. We first define a strong bisimulation for open pNets. In practice, as happens in
+process algebras, strong bisimulation is too strong, and we need to define some coarser
+relations, taking into account invisible or internal moves. We then define an
+equivalence relation similar to the classical \emph{weak bisimulation}, and study its
+properties. Among these properties we are interested in compositionality: If two systems
+are proven equivalent they will be undistinguishable by their context, and they will
+also be undistinguishable when their holes are filled with equivalent systems.
 The article is illustrated with a transport protocol running example; it shows the characteristics of our formalism and our bisimulation relations.
@@
 \begin{figure}[t]
-   \includegraphics[width=.37\textwidth]{XFIG/SimpleProt-Schema}
-   \includegraphics[width=.62\textwidth]{XFIG/SimpleProt2-Spec}
+   \includegraphics[width=.37\textwidth]{SimpleProt-Schema.pdf}
+   \includegraphics[width=.62\textwidth]{SimpleProt2-Spec.pdf}
    \caption{pNet structure of the example and specification expressed as a pNet}
@@
 \begin{figure}[t]
-  \centerline{\includegraphics[width=.9\textwidth]{XFIG/SimpleProt2-pNet-tau}}
+  \centerline{\includegraphics[width=.9\textwidth]{SimpleProt2-pNet-tau.pdf}}
   \caption{Composed pNet with the Simple Protocol Implementation}  \label{SimpleProt:Impl}
@@
 \begin{minipage}{0.30\linewidth}
-	\includegraphics[width=\linewidth]{XFIG/Bisim}
+	\includegraphics[width=\linewidth]{Bisim.pdf}
 \end{minipage}
@@
 \begin{figure}[ht]
-   \centerline{\includegraphics[width=13cm]{XFIG/SPSpecOpen}}
+   \centerline{\includegraphics[width=13cm]{SPSpecOpen.pdf}}
    \caption{Specification Open Automaton}
@@
  \begin{figure}[ht]
-  \centerline{\includegraphics[width=15cm]{XFIG/SPImplOpen}}
+  \centerline{\includegraphics[width=15cm]{SPImplOpen.pdf}}
   \caption{Open Automaton of the Simple Protocol Implementation}  \label{SimpleProtCounter:ImplOA}
@@
 \begin{figure}[ht]
-   \centerline{\includegraphics[width=13cm]{XFIG/WOT2-result}}
+   \centerline{\includegraphics[width=13cm]{WOT2-result.pdf}}
   \caption{Construction of an example of weak open transition}
@@
 \begin{figure}[h]
-   \centerline{\includegraphics[width=15cm]{XFIG/SPSpecWeakOpen}}
+   \centerline{\includegraphics[width=15cm]{SPSpecWeakOpen.pdf}}
   \caption{Weak Open Automaton of the Specification}
@@
 %\begin{figure}[h]
-  % \centerline{\includegraphics[width=11cm]{XFIG/SimpleProtImpl-WOA}}
+  % \centerline{\includegraphics[width=11cm]{SimpleProtImpl-WOA}}
  % \caption{Weak Open Automaton of the implementation}
@@
 \begin{figure}[h]
-   \centerline{\includegraphics[width=11cm]{XFIG/SimpleProtImpl-WOA2}}
+   \centerline{\includegraphics[width=11cm]{SimpleProtImpl-WOA2.pdf}}
   \caption{Weak Open Automaton of the implementation}
@@
 
-\ERIC{ To the best of our knowledge, there are not many research works on Weak Bisimulation Equivalences between such complicate system models (open, symbolic, data-aware, with loops and assignments).
-We give a brief overview of other related publications, focussing first on Open and Compositional approaches, then on Symbolic Bisimulation for data-sensitive systems.}
+ To the best of our knowledge, there are not many research works on Weak Bisimulation Equivalences between such complicate system models (open, symbolic, data-aware, with loops and assignments).
+We give a brief overview of other related publications, focussing first on Open and Compositional approaches, then on Symbolic Bisimulation for data-sensitive systems.
 
@@
 %\TODO{retravailler le paragraphe ci dessous: faire ref a Facs-2013 (reconfig ds pNets) - virer 14 (probabilistic) ?} \cite{GasparHM:2013}
-\ERIC{In
+In
 \cite{Johnson:2013:CBSE,Johnson:2014:qosa}, the authors investigate several methodologies for the compositional verification of software systems, with the aim to verify reconfigurable component systems.
@@
 are quite different from ours, in particular they are much less structured, and translating them is clearly outside the scope of this article.
-In previous work \cite{gaspar:hal-00916115}, we also have shown how (closed) pNet models could be used to encode and verify finite instances of reconfigurable component systems. }
+In previous work \cite{gaspar:hal-00916115}, we also have shown how (closed) pNet models could be used to encode and verify finite instances of reconfigurable component systems. 
 %Additionally, the more compositional constraint resolution provided by the authors could also be interesting to make our SMT proofs scale better (inside a single pNet for example), the integration of the Z3 framework described in \cite{Johnson:2014:qosa} with our proof theory for open pNets would also be worth investigating from a practical point of view.
@@
 \subsubsection*{Symbolic and data-sensitive systems}
-\ERIC{ As mentioned in the \emph{Introduction}, the work that brought us a lot of inspirations are those of Lin et al.
+ As mentioned in the \emph{Introduction}, the work that brought us a lot of inspirations are those of Lin et al.
 \cite{IngolfsdottirL:2001,HennessyLin:TCS95,Linconcur96}.
@@
 Then our settings for management of data types are much less restrictive, thanks to our use of satisfiability engines, while Lin's algorithms were limited to data-independent systems.
-}
 
@@
 We are currently extending this work,  looking at  both further properties of FH-bisimulation, but also
-the relations with existing equivalences on both closed and open systems. \ERIC{In particular, our model being significantly different from those considered in \cite{IngolfsdottirL:2001}, it
-would be interesting to compare our "FH" family of bisimulations with the hierarchy of symbolic bisimulations from these authors.}
+the relations with existing equivalences on both closed and open systems. In particular, our model being significantly different from those considered in \cite{IngolfsdottirL:2001}, it
+would be interesting to compare our "FH" family of bisimulations with the hierarchy of symbolic bisimulations from these authors.
 We also plan to apply open pNets to the study of complex composition
@@
 \begin{center}
-\includegraphics[width=6cm]{XFIG/proof-explain}
+\includegraphics[width=6cm]{proof-explain.pdf}
 \end{center}\caption{Composition of the subsequences}\label{figproof}
@@
 &=\Pred_Q\land\Pred\land \alpha_Q=\beta_{j_0}\\[.3ex]
-\Post_c&=\Post\uplus\Post_Q \qedhere
+\Post_c&=\Post\uplus\Post_Q 
 \end{split}
@@
 %% \begin{figure}[t]
-%%    \includegraphics[width=5.5cm]{XFIG/SimpleProt-Schema}
-%%    \includegraphics[width=6.5cm]{XFIG/SimpleProt2-Spec}
+%%    \includegraphics[width=5.5cm]{SimpleProt-Schema}
+%%    \includegraphics[width=6.5cm]{SimpleProt2-Spec}
 %%    \caption{Specification pNet Schema and Specification}
@@
 %% \begin{figure}[t]
-%%   \centerline{\includegraphics[width=12cm]{XFIG/SimpleProt2-pNet}}
+%%   \centerline{\includegraphics[width=12cm]{SimpleProt2-pNet}}
 %%   \caption{Composed pNet with the Simple Protocol Implementation}  \label{App:SimpleProt:Impl}
@@
 \begin{figure}[h]
-   \centerline{\includegraphics[width=10cm]{XFIG/SimpleProtImpl-WOA2}}
+   \centerline{\includegraphics[width=10cm]{SimpleProtImpl-WOA2.pdf}}
    \caption{Weak Open Automaton of the implementation}

### 2020-07-24 2016-Weak-FH-Bisim/Coverletter.tex
first vesrsion

\documentclass[10pt]{article}
\usepackage[latin1]{inputenc} 
\usepackage{alltt,url}
%% Old ttbox definition without frame:
\newenvironment{ttbox}{\begin{alltt}\small\tt}%
                      {\end{alltt}}

\thispagestyle{empty}
\addtolength{\textheight}{2cm}
\begin{document}
\section*{Cover Letter }
\subsection*{Submission to Logical Methods in Computer Science}
\medskip
\begin{ttbox}
Title: Compositional equivalences based on Open pNets
Authors: R. Ameur-Boulifa, L. Henrio, and E. Madelaine
\end{ttbox}
\bigskip
%\subsubsection*{Letter to Reviewers and Editors}
Dear reviewers and editors,

\medskip
This article defines bisimulation relations  for the comparison of systems specified as parameterised Networks of synchronised automata; it formalises the work we did in the last 4 years theory for the operators composing concurrent processes. This theory is based on the definition of operators as open processes. By defining the operational semantics of open processes, using open transitions that include symbolic hypotheses on the behaviour of the holes.

\smallskip

We think this article fits with the scope and criteria of ``Logical Methods in Computer Science'' for the following reasons. First, to our knowledge this is the first paper we propose a theoretical framework for analysing the behaviour of open systems modelled as pNets, i.e., open terms of suitable process calculi.
The  semantics of pNets is given by means of a symbolic open transition system. Behavioural equivalences for pNets, like strong and weak bisimilarities, are defined over such a open transition systems.

\smallskip

Concerning prior publications Forte'16, we have already defined a theory for the operators composing concurrent processes. The theory is based on the definition of operators as open pNets. However, the study of compositionability was only partial, and in particular the proof that bisimulation is an equivalence that is one new contribution of this article.....

\smallskip

Considering the length of the submitted material, we suggest that we
leave only the two first appendices in the final version of the paper (leading to a
paper of 73 pages) because they are crucial to understand the paper.
The other appendices will be available as a research report, we keep
them in the submission to ease the work of the reviewers. %Of course, depending on the opinion of the reviewers, we will also move more or less material in the body of the paper, in the appendices, or to the research report.

\begin{flushright}
  Best Regards,\\
  Rab\'ea Ameur-Boulifa, Ludovic Henrio, and Eric Madelaine
\end{flushright}
\end{document}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2020-07-24 2016-Weak-FH-Bisim/Coverletter.tex
coverletter V2

@@
 \medskip
-This article defines bisimulation relations  for the comparison of systems specified as parameterised Networks of synchronised automata; it formalises the work we did in the last 4 years theory for the operators composing concurrent processes.
+This article defines bisimulation relations  for the comparison of systems specified as parameterised Networks of synchronised automata; it formalises the work we did in the last 4 years and provides a theory for the operators composing concurrent processes.
 This theory is based on the definition of operators as open processes.
-By defining the operational semantics of open processes, using open transitions that include symbolic hypotheses on the behaviour of the holes.
+We define the operational semantics of open processes, using open transitions that include symbolic hypotheses on the behaviour of the holes.The  semantics of pNets is given by means of a symbolic open transition system.
+Behavioural equivalences for pNets, like strong and weak bisimilarities, are defined over such a open transition systems.
+We finally prove that these equivalences are compositional.
 
@@
 First, to our knowledge this is the first paper we propose a theoretical framework for analysing the behaviour of open systems modelled as pNets, i.e., open terms of suitable process calculi.
-The  semantics of pNets is given by means of a symbolic open transition system.
-Behavioural equivalences for pNets, like strong and weak bisimilarities, are defined over such a open transition systems.
+Second, the quite theoretical and fundamental approach adopted in this paper fits well to the topics of LMCS.
+Finally, because we already applied pNets and their equivalence relations to the verification of concrete cases and because we illustrate our approach on a small but realistic example, we believe our article illustrates well the applicability of the theory we propose.
 
@@
 
-Concerning prior publications Forte'16, we have already defined a theory for the operators composing concurrent processes.
+Concerning prior publications, in Forte'16, we have already defined a theory for the operators composing concurrent processes.
 The theory is based on the definition of operators as open pNets.
-However, the study of compositionability was only partial, and in particular the proof that bisimulation is an equivalence that is one new contribution of this article.....
+However, the study of compositionability was only partial, and in particular the proof that bisimulation is an equivalence that is one new contribution of this article.
+Additionally, previous works only formalised strong bisimulation, and the formalisation and proofs dealing with weak bisimulation are also new here.
 
@@
 
-Considering the length of the submitted material, we suggest that we
-leave only the two first appendices in the final version of the paper (leading to a
-paper of 73 pages) because they are crucial to understand the paper.
+Considering the length of the submitted material,
+ we   suggest to
+keep the two first appendices in the final version of the paper (leading to a
+paper of 73 pages) because they are important to understand the paper.
 The other appendices will be available as a research report, we keep
 them in the submission to ease the work of the reviewers. 
-%Of course, depending on the opinion of the reviewers, we will also move more or less material in the body of the paper, in the appendices, or to the research report.
+Of course, depending on the opinion of the reviewers, we could also move more material to  the body of the paper, or remove more proofs from the published version and only keep them in the report.
 

### 2020-09-03 2016-Weak-FH-Bisim/WeakBisim.tex
quelques states variables, et autres details...

@@
    \mathcal{T}_1\!>$ and $A_2 = <\!J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2\!>$
-   are open automata with identical holes of the same sort, with disjoint state variables.
+   are open automata with identical holes of the same sort, with disjoint sets of variables.
 
@@
 The resulting behaviour is quite simple:  we have a main loop including receiving a message from $P$ and transmitting the same message to $Q$, with some intermediate $\tau$ actions from the internal communications between the protocol processes.
-In most of the transitions, you can observe that data is propagated between the successive state variables (holding the message, and the error counter value).
+In most of the transitions, you can observe that data is propagated between the successive plts variables (holding the message, and the error counter value).
 On the right of the figure, you have a loop of $\tau$ actions ($\texttt{SI}_4$, $\texttt{SI}_5$ and $\texttt{SI}_6$)  showing the handling of errors and corresponding increments of the error counter.
@@
 First, let us point out that the weak OT loops ($WI_1$,$WI_2$ and $W_\tau$) on state ${000}$ are also present in all other states, we did not repeat them.
-Then many WOTs are similar, and numbered accordingly as 3, 3a, 3b, 3c and 8, 8a, 8b, 8c respectively: they only differ by the name of the state variables in their respective source or target states; the "variant" WOTs appear in blue in   Figure \ref{SimpleProtCounter:ImplWOA2}.
+Then many WOTs are similar, and numbered accordingly as 3, 3a, 3b, 3c and 8, 8a, 8b, 8c respectively: they only differ by the name of the \TODO{ state variables} in their respective source or target states; the "variant" WOTs appear in blue in   Figure \ref{SimpleProtCounter:ImplWOA2}.
 \end{example}
@@
 Let $A_1 = <J,\mathcal{S}_1, s_0,V_1,
-    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0, V_2, \mathcal{T}_2>$ be open automata with disjoint state variables.
+    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0, V_2, \mathcal{T}_2>$ be open automata with disjoint sets of variables.
 Let $<J,\mathcal{S}_1, s_0,V_1,
@@
 This drawing is based on the observation that states 202 and 000 are only linked by a "pure $\tau$" transition, and have exactly the same possible behaviours.
-More tricky, they do not have the same state variables, as 202 has the variables of state $s2$, but none of these variables are used in transitions from 202.
+%More tricky, they do not have the same state variables, as 202 has the variables of state $s2$, but none of these variables are used in transitions from 202.
 In this configuration we can guarantee that they are Weak bisimilar, and we have merged their (incoming and outgoing) transitions in the Figure. We denote this 

### 2020-09-03 2016-Weak-FH-Bisim/WeakBisim.tex
modif figures + details

@@
 \begin{figure}[t]
-  \centerline{\includegraphics[width=.9\textwidth]{XFIG/SimpleProt2-pNet-tau}}
+  \centerline{\includegraphics[width=.95\textwidth]{XFIG/SimpleProt2-pNet-tau}}
   \caption{Composed pNet with the Simple Protocol Implementation}  \label{SimpleProt:Impl}
@@
 			(\texttt{b\_ec}\gets \texttt{b\_ec}+2) }
-         {\text{b1} \OTWeakarrow \tau \text{b1}}$. We can  can iterate this construction an arbitrary number of times, getting for any natural number $n$ the weak open transition:
+         {\text{b1} \OTWeakarrow \tau \text{b1}}$. We can iterate this construction an arbitrary number of times, getting for any natural number $n$ a weak open transition:
   $\openrule
@@
 Finally,  applying again \WTTrois, and using the central open transition having \texttt{\nounderline{out(b\_msg,b\_ec)}}  as $\alpha$, we get the resulting weak open transition between b1 and b0 (as shown in Figure \ref{WOT2}).
-Applying the substitutions finally yields the weak transition $WS_7$ in Figure  \ref{SimpleProtCounter:WeakSpecOA}.
+Applying the substitutions finally yields the weak transitions family $WS_7$ in Figure  \ref{SimpleProtCounter:WeakSpecOA}.
 
@@
     or as input variables in a pLTS, as \texttt{?msg} in \texttt{M1}.
-  \item The variables in the guards of synchronisation vectors do not need to be explicitly quantified: all variables in a guard that do not appear inside the vector actions will be recognised as bound by a \emph{forall} quantifier inside the guard.
+  \item The variables in the guards of synchronisation vectors do not need to be explicitly quantified: by convention, all variables in a guard that do not appear inside the vector actions will be recognised as bound by a \emph{forall} quantifier inside the guard.
     \item The tools will check that everything is correctly declared, and that variables are used properly and do not conflict between different objects, that vectors have coherent length, etc.

### 2020-09-04 2016-Weak-FH-Bisim/WeakBisim.tex
Some overfull hbox

@@
 \[
-\begin{array}[l]{rcl@{\quad}p{5.5cm}}
+\begin{array}[l]{rcl@{\quad}p{7.5cm}}
   \alpha\in\AlgA&::=&a(p_1,\ldots,p_n)&\text{action terms}\\
@@
 \noindent
-\begin{minipage}{0.69\linewidth} 	Suppose 
+\begin{minipage}{0.67\linewidth} 	Suppose 
    $A_1 = <\!J,\mathcal{S}_1, s_0,V_1,
@@
 \Leaves(\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in 
-    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
-k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
+    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \quad  	
+k\!\in\! K \quad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
 \\
@@
   Let $A = <J,\mathcal{S},s_0,V,\mathcal{T}>$ be an open automaton. 
-The weak open automaton \emph{derived} from $A$ is an open automaton  $<J,\mathcal{S},s_0,V,\WT>$ where $\WT$ is derived from $\mathcal{T}$ by saturation, applying the following rules.
+The weak open automaton \emph{derived} from $A$ is an open automaton  $<J,\mathcal{S},s_0,V,\WT>$ where $\WT$ is derived from $\mathcal{T}$ by saturation, applying the following rules:
 %\noindent{\bf Invisible $\tau$ transitions:}
@@
    \medskip     
-The  \Post~of the weak OT $ WI_{6a}$ is:\\
-
-$
+The  \Post~of the weak OT $ WI_{6a}$ is:
+
+$$
 \begin{array}{ll}
@@
 \end{array}
-$
+$$
 
@@
 Either we define a simulation similar to the strong simulation but based on open automata, this would look like the FH-simulation but would need to be adapted to weak open transitions.
-Or we define directly and classically a weak FH-simulation as a relation between two open automata, relating the open transition of one open automaton with the transition of the weak open automaton derived from the second one.
+Or we define directly and classically a weak FH-simulation as a relation between two open automata, relating the open transition of the first one with the transition of the weak open automaton derived from the second one.
 
@@
 \{j_0\}$; we denote $I'_1=I_1\setminus \{j_0\}$ the predicate is 
-$\displaystyle{\Pred\,'=\!\!\!\!\!\bigwedge_{m\in I_1'\uplus I_2}\!\!\!\!\!\Pred_m  \land \Predsv(SV_k,\alpha_m^{m \in I'_1\uplus I_2},\beta_j^{j\in J\cup \{j_0\}},\alpha)}$
+$\displaystyle{\Pred\,'=\!\!\!\!\!\bigwedge_{m\in I_1'\uplus I_2}\!\!\!\!\!\Pred_m  \land \Predsv(SV_k,\alpha_m^{m \in I'_1\uplus I_2},\beta_j^{j\in J\cup \{j_0\}},\alpha)}$\\
 where\footnotemark[\thefootnote] $\Predsv(SV_k,\alpha_m^{m \in I'_1\uplus I_2},\beta_j^{j\in 
@@
 
+  \subsection{Test}
+
+  $<1,2,3>$
+
+  $\left< 1,2,3 \right>$
+
 \end{document}

### 2020-09-04 2016-Weak-FH-Bisim/WeakBisim.tex
un peu mieux sur les espaces entre trucs
apres le skype: automates et espaces

@@
 \set{\Sort},
-\set{\symb{SV}}\myrangle)
-=\{\alpha' |\, \SV{\set{\alpha}}{\alpha'}{e_b}\in\set{\symb{SV}}\}
+\set{\symb{SV}\,}\myrangle)
+=\{\alpha' |\, \SV{\set{\alpha}}{\alpha'}{e_b}\in\set{\symb{SV}}\,\}
 \end{array}
@@
 \Leaves(\mylangle \pNet_i^{i\in I}\!,%Sort_j^{j\in J}
-\set{\Sort}\!, \set{\symb{SV}}\myrangle) = {\displaystyle \biguplus_{i\in 
+\set{\Sort}\!, \set{\symb{SV}\,}\myrangle) = {\displaystyle \biguplus_{i\in 
 I}\Leaves(\pNet_i)\uplus\{i\mapsto \pNet_i|\pNet_i \text{ is a }\pLTS\}}
@@
 	An open pNet: $\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
-	\set{\symb{SV}}\myrangle$
+	\set{\symb{SV}}\,\myrangle$
  can be (partially) filled by providing  a pNet $\pNetQ$ of the
@@
 	\pNet_i^{i\in I}\uplus\{j_0\mapsto \pNetQ\},\Sort_j^{j\in J\setminus \{j_0\}},
-	\set{\symb{SV}}\myrangle
+	\set{\symb{SV}}\,\myrangle
 	\]
@@
 	An \emph{open automaton} is a structure\\ $A =
-	<\!J,\mathcal{S},s_0,V,\mathcal{T}\!>$ where:
+	\mylangle J,\mathcal{S},s_0,V,\mathcal{T}\myrangle$ where:
 	\begin{itemize}
@@
            \set{\beta}\subst{\Post}, \Pred\,'\subst{\Post}\land\Pred,\Post\shortotimes\Post\,'}
-         {t \OTarrow {\alpha\subst{\Post}} {t'}}\in\mathcal{T}
+         {\raisemath{-2pt}{t \OTarrow {\alpha\subst{\Post}} {t'}}{}}
+ \in\mathcal{T}
 \end{mathpar}
@@
 
-A relation over the states of two open automata  $<\!J,\mathcal{S}_1, s_0,V_1,
-   \mathcal{T}_1\!>$ and $<\!J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2\!>$ has the form $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$, it relates states of $\mathcal{S}_1$ and 
+A relation over the states of two open automata  $\mylangle J,\mathcal{S}_1, s_0,V_1,
+   \mathcal{T}_1 \myrangle$ and $\mylangle !J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2 \myrangle$ has the form $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$, it relates states of $\mathcal{S}_1$ and 
 $\mathcal{S}_2$ constrained by a predicate.
@@
 \begin{minipage}{0.67\linewidth} 	Suppose 
-   $A_1 = <\!J,\mathcal{S}_1, s_0,V_1,
-   \mathcal{T}_1\!>$ and $A_2 = <\!J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2\!>$
+   $A_1 = \mylangle J,\mathcal{S}_1, s_0,V_1,
+   \mathcal{T}_1 \myrangle$ and $A_2 = \mylangle J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2 \myrangle$
    are open automata with identical holes of the same sort, with disjoint sets of variables.
@@
 	\label{def:operationalSemantics} The semantics of a pNet $\pNet$ is an open automaton $A\!= 
-	<\!\!Holes(\pNet),States(\pNet),InitState(\pNet),vars(P),\mathcal{T}\!\!>$ where $\mathcal{T}$   is the smallest set of open transitions such that $\mathcal{T}=\{OT\,|\,\pNet \models OT \}$ and	$\pNet \models OT$	is defined by the following  rules:
+	\mylangle \symb{Holes}(\pNet),\symb{States}(\pNet),\symb{InitState}(\pNet),\symb{vars}(P),\mathcal{T} \myrangle$ where $\mathcal{T}$   is the smallest set of open transitions such that $\mathcal{T}=\{OT\,|\,\pNet \models OT \}$ and	$\pNet \models OT$	is defined by the following  rules:
 %	\begin{itemize}
@@
 \begin{mathpar}
-    \mprset {vskip=.8ex}
+    \mprset {vskip=.45ex}
 \inferrule
     {
-\Leaves(\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in 
-    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \quad  	
+\Leaves(\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{\,k\in 
+    	K}\myrangle) \!=\! \pLTS_l^{\,l\in L} \quad  	
 k\!\in\! K \quad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
@@
 	\models\openrule
-    	{
-    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
+    	{\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
     	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
@@
     }
-    {\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
+    {\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{\,k\in K}\myrangle
     	\models
@@
 \begin{definition}[Non-observability of $\tau$ actions for open automata]\label{def:Non-ObsTau}
-An open automaton $A = <J,\mathcal{S},s_0,V,\mathcal{T}>$ \emph{cannot observe $\tau$ actions} if and only if for all $j$ in $J$ and $s$ in $\mathcal{S}$ we have:
+An open automaton $A = \mylangle J,\mathcal{S},s_0,V,\mathcal{T}\myrangle$ \emph{cannot observe $\tau$ actions} if and only if for all $j$ in $J$ and $s$ in $\mathcal{S}$ we have:
 \begin{enumerate}
@@
 
-A weak open automaton $<J,\mathcal{S},s_0,V,\WT>$ is similar to an open automaton  except that $\WT$ is a set of weak open transitions over $J$ and $\mathcal{S}$.
+A weak open automaton $\mylangle J,\mathcal{S},s_0,V,\WT\myrangle$ is similar to an open automaton  except that $\WT$ is a set of weak open transitions over $J$ and $\mathcal{S}$.
 \end{definition}
@@
 \begin{definition}[Building a weak open automaton]\label{def:buildweakOT}
-  Let $A = <J,\mathcal{S},s_0,V,\mathcal{T}>$ be an open automaton. 
-The weak open automaton \emph{derived} from $A$ is an open automaton  $<J,\mathcal{S},s_0,V,\WT>$ where $\WT$ is derived from $\mathcal{T}$ by saturation, applying the following rules:
+  Let $A = \mylangle J,\mathcal{S},s_0,V,\mathcal{T}\myrangle$ be an open automaton. 
+The weak open automaton \emph{derived} from $A$ is an open automaton  $\mylangle J,\mathcal{S},s_0,V,\WT\myrangle$ where $\WT$ is derived from $\mathcal{T}$ by saturation, applying the following rules:
 %\noindent{\bf Invisible $\tau$ transitions:}
@@
 \begin{mathpar}
-  \mprset {vskip=.5ex}
 \inferrule{
@@
 \begin{mathpar}
-  \mprset {vskip=.5ex}
 \inferrule {\openrule
@@
 First, let us point out that the weak OT loops ($WI_1$,$WI_2$ and $W_\tau$) on state ${000}$ are also present in all other states, we did not repeat them.
-Then many WOTs are similar, and numbered accordingly as 3, 3a, 3b, 3c and 8, 8a, 8b, 8c respectively: they only differ by the name of the \TODO{ state variables} in their respective source or target states; the "variant" WOTs appear in blue in   Figure \ref{SimpleProtCounter:ImplWOA2}.
+Then many WOTs are similar, and numbered accordingly as 3, 3a, 3b, 3c and 8, 8a, 8b, 8c respectively: they only differ by their respective source or target states; the "variant" WOTs appear in blue in   Figure \ref{SimpleProtCounter:ImplWOA2}.
 \end{example}
@@
 
-Then the effect of one single $100 \xrightarrow{OT_4} 210 \xrightarrow{OT_5} 220 \xrightarrow{OT_6} 100$ loop is:
-\smallskip
-
-$post_{456} = post_6 \shortotimes\ post_5 \shortotimes\ post_4
-= (\texttt{s\_ec}\gets \texttt{s\_ec}+1)$.
-\footnote{when showing  the result of $Posts$ composition, we will omit the identity substitutions introduced by the $\shortotimes$ definition in page \pageref{def:substitutions}}
-\medskip
+Then the effect of one single $100 \xrightarrow{OT_4} 210 \xrightarrow{OT_5} 220 \xrightarrow{OT_6} 100$ loop is\footnote{when showing  the result of $Posts$ composition, we will omit the identity substitutions introduced by the $\shortotimes$ definition in page \pageref{def:substitutions}}:
+\[post_{456} = post_6 \shortotimes\ post_5 \shortotimes\ post_4
+= (\texttt{s\_ec}\gets \texttt{s\_ec}+1)\]
 
@@
 The  \Post~of the weak OT $ WI_{6a}$ is:
-
 $$
-\begin{array}{ll}
+\begin{array}{l@{}l}
 Post_{6a}&= post_{4}\shortotimes\ post_{456*}\shortotimes\ post_{6}\\ 
@@
 \noindent
-Let $A_1 = <J,\mathcal{S}_1, s_0,V_1,
-    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0, V_2, \mathcal{T}_2>$ be open automata with disjoint sets of variables.
-Let $<J,\mathcal{S}_1, s_0,V_1,
-    \WT_1>$ and $<J,\mathcal{S}_2,t_0, V_2, \WT_2>$ be the
+Let $A_1 = \mylangle J,\mathcal{S}_1, s_0,V_1,
+    \mathcal{T}_1\myrangle$ and $A_2 = \mylangle J,\mathcal{S}_2,t_0, V_2, \mathcal{T}_2\myrangle$ be open automata with disjoint sets of variables.
+Let $\mylangle J,\mathcal{S}_1, s_0,V_1,
+    \WT_1\myrangle$ and $\mylangle J,\mathcal{S}_2,t_0, V_2, \WT_2\myrangle$ be the
 weak open automata derived from $A_1$ and $A_2$ respectively.
@@
 \end{mathpar}
- such that  $\forall x, \{j\in J'|\beta_j\neq\tau\}=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
+ such that  $\forall x.\, \{j\in J'|\beta_j\neq\tau\}=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
  and  \\
@@
 \begin{definition}[Semantics of pNets as a weak open automaton]
-Let $A$ be the open automaton expressing the semantics of an open pNet $\pNet$; let $<J,\mathcal{S},s_0, V, \WT>$ be the weak open automaton derived from $A$; this weak open automaton defines the weak semantics of the pNet $\pNet$.
+Let $A$ be the open automaton expressing the semantics of an open pNet $\pNet$; let $\mylangle J,\mathcal{S},s_0, V, \WT\myrangle$ be the weak open automaton derived from $A$; this weak open automaton defines the weak semantics of the pNet $\pNet$.
 Then, we denote $\pNet \models \WOT$ whenever $\WOT\in\WT$.
@@
 $\displaystyle{\Pred\,'=\!\!\!\!\!\bigwedge_{m\in I_1'\uplus I_2}\!\!\!\!\!\Pred_m  \land \Predsv(SV_k,\alpha_m^{m \in I'_1\uplus I_2},\beta_j^{j\in J\cup \{j_0\}},\alpha)}$\\
-where\footnotemark[\thefootnote] $\Predsv(SV_k,\alpha_m^{m \in I'_1\uplus I_2},\beta_j^{j\in 
+where
+\begin{multline*}
+\Predsv(SV_k,\alpha_m^{m \in I'_1\uplus I_2},\beta_j^{j\in 
 J\cup 
-\{j_0\}},\alpha)\Leftrightarrow 
+\{j_0\}},\alpha)\Leftrightarrow \\
 \forall i\in I'_1\uplus I_2.\, \alpha_i=\alpha'_i\land \forall j \in J\cup \{j_0\}.\, 
@@
 \alpha=\alpha'
-\land e_b$. Modulo renaming of fresh variables, this is identical to the predicate that 
+\land e_b
+\end{multline*}
+
+ Modulo renaming of fresh variables, this is identical to the predicate that 
 occurs in 
@@
 \begin{lemma}[Alternative definition of weak open transitions]
-\label{lem-rel-OT-WOT} Let $A = <J,\mathcal{S}, s_0,V_1,
-    \mathcal{T}>$ be open automata and $<J,\mathcal{S}, s_0,V_2,
-    \WT>$ be the
+\label{lem-rel-OT-WOT} Let $A = \mylangle J,\mathcal{S}, s_0,V_1,
+    \mathcal{T}\myrangle$ be open automata and $\mylangle J,\mathcal{S}, s_0,V_2,
+    \WT\myrangle$ be the
 weak open automata derived from $A$.  The two following statements are equivalent
@@
 				 } {s_{10} \OTWeakarrow {\tau}s_{11}}\! \in\! \WT
-\quad
+\\
 \openrule
@@
 				 } {s'' \OTWeakarrow {\alpha'} s'}\! \in\!\WT
-\quad
+\\
 \openrule
@@
 \\
-\set{\gamma''}= \vis{\set{\beta_{10}}} \dotcup \set{\gamma}\subst{\Post_{10}}\quad
+\set{\gamma''}= \vis{\set{\beta_{10}}} \dotcup \set{\gamma}\subst{\Post_{10}}\\
 \Pred\,''=\Pred_{10}\land\Pred\subst{\Post_{10}}\\%\land (\Pred_3\subst{\Post_2})\subst{\Post_{10}}
-\Post\,''=\Id(s'')\shortotimes\Post\shortotimes\Post_{10} \quad \alpha''=\alpha'\subst{\Post_{10}}
+\Post\,''=\Id(s'')\shortotimes\Post\shortotimes\Post_{10} \\ \alpha''=\alpha'\subst{\Post_{10}}
 }
@@
          {s \OTWeakarrow {\tau} s'} \in \WT
-\quad
+\\
 \openrule
@@
          {s' \OTWeakarrow {\alpha} s''} \in \WT
-\quad
+\\
 \openrule
@@
 
- Let $A_1 = <\!J,\mathcal{S}_1, s_0, V_1,
-    \mathcal{T}_1\!>$ and $A_2 = <\!J,\mathcal{S}_2,t_0, V_2, \mathcal{T}_2\!>$ be open automata; $<\!J,\mathcal{S}_1, s_0,V_1,
-    \WT_1\!>$ and $<\!J,\mathcal{S}_2,t_0, V_2, \WT_2\!>$ be the
+\fussy
+ Let $A_1 = \mylangle J,\mathcal{S}_1, s_0, V_1,
+    \mathcal{T}_1\myrangle$ and $A_2 = \mylangle J,\mathcal{S}_2,t_0, V_2, \mathcal{T}_2 \myrangle$ be open automata; $\mylangle J,\mathcal{S}_1, s_0,V_1,
+    \WT_1\myrangle$ and $\mylangle J,\mathcal{S}_2,t_0, V_2, \WT_2\myrangle$ be the
 weak open automata derived from $A_1$ and $A_2$ respectively.
@@
    have:
+\sloppy
 \begin{itemize}
@@
 Because 
-
-$Post_{6a}=\ post_{4}\shortotimes\ post_{456}^*\shortotimes\ post_{6}\\
-= \left( (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec})
+\begin{align*}
+Post_{6a}&=\ post_{4}\shortotimes\ post_{456}^*\shortotimes\ post_{6}\\
+&= \left( (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec})
 \shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+n) \right)
 \shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+1) \\
-= (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets (\texttt{s\_ec}+1)+n, \texttt{s\_ec}\gets (\texttt{s\_ec}+1)+n)$
-
-\medskip
+&= (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets (\texttt{s\_ec}+1)+n, \texttt{s\_ec}\gets (\texttt{s\_ec}+1)+n)
+\end{align*}
+
 $ WI_{456*}(n) = \openrule

### 2020-09-07 2016-Weak-FH-Bisim/WeakBisim.tex
texttt dans examples

@@
 			(\texttt{b\_ec}\gets \texttt{b\_ec}+1) }
-         {\text{b1}\OTWeakarrow \tau \text{b1}}$; $\openrule
+         {\texttt{b1}\OTWeakarrow \tau \texttt{b1}}$; $\openrule
          {\{\}, True,
 			(\texttt{b\_ec}\gets \texttt{b\_ec}+1) }
-         {\text{b1} \OTWeakarrow \tau \text{b1}}$;  $\openrule
+         {\texttt{b1} \OTWeakarrow \tau \texttt{b1}}$;  $\openrule
          {\{\}, True,
 			() }
-         {\text{b1} \OTWeakarrow \tau \text{b1}}$. Then Rule \WTTrois~ produces  $\openrule
+         {\texttt{b1} \OTWeakarrow \tau \texttt{b1}}$. Then Rule \WTTrois~ produces  $\openrule
          {\{\}, True,
 			(\texttt{b\_ec}\gets \texttt{b\_ec}+2) }
-         {\text{b1} \OTWeakarrow \tau \text{b1}}$. We can iterate this construction an arbitrary number of times, getting for any natural number $n$ a weak open transition:
+         {\texttt{b1} \OTWeakarrow \tau \texttt{b1}}$. We can iterate this construction an arbitrary number of times, getting for any natural number $n$ a weak open transition:
   $\openrule
@@
 			(\texttt{ec}\gets \texttt{ec}+n) }
-        {\text{b1} \OTWeakarrow \tau \text{b1}}\, \forall n \geq 0$.
+        {\texttt{b1} \OTWeakarrow \tau \texttt{b1}}\, \forall n \geq 0$.
 Finally,  applying again \WTTrois, and using the central open transition having \texttt{\nounderline{out(b\_msg,b\_ec)}}  as $\alpha$, we get the resulting weak open transition between b1 and b0 (as shown in Figure \ref{WOT2}).
@@
 
-$ \forall n\ge 0. WI_3(n) = \openrule
+$ \forall n\ge 0.\, WI_3(n) = \openrule
   {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
@@
 
-$  \forall n\ge 0. WI_4(n) = \openrule
+$  \forall n\ge 0.\, WI_4(n) = \openrule
          {\{\}, True, 
@@
 
-$  \forall n\ge 0. WI_{456}(n) = \openrule
+$  \forall n\ge 0.\, WI_{456}(n) = \openrule
          {\{\}, True, 

### 2020-09-08 2016-Weak-FH-Bisim/WeakBisim.tex
formules

@@
 \item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
-  synchronisation vectors. $\forall k\!\in\! K,
+  synchronisation vectors. $\forall k\!\in\! K.\,
   \symb{SV}_k\!=\!\SV{\alpha_{l}^{l\in I_k \uplus J_k}}{\alpha'_k}{e_k}$ where
@@
 \end{mathpar}
- such that  $\forall x, J'=J_{x}$ and there exists $\Pred_{s',t_x}$ such that $(s',t_x|\Pred_{s',t_x})\in 
+ such that  $\forall x.\, J'=J_{x}$ and there exists $\Pred_{s',t_x}$ such that $(s',t_x|\Pred_{s',t_x})\in 
  \mathcal{R}$
@@
 
-$ \forall n\ge 0. WI_{6a}(n) = \openrule
+$ \forall n\ge 0.\, WI_{6a}(n) = \openrule
          {\{\}, True, 
@@
       \begin{multline*}
-\forall fv_{OT}. \Big\{ \Pred \land \Pred_{OT} \implies\\
+\forall fv_{OT}.\, \Big\{ \Pred \land \Pred_{OT} \implies\\
  \bigvee_{x\in X}\!
@@
   \item The verification condition \\
-    $\forall fv_{OT}. \{ \Pred \land \Pred_{OT}\\
+    $\forall fv_{OT}.\, \{ \Pred \land \Pred_{OT}\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
@@
 
-$\forall \texttt{m1}. \{True \land True\hspace{3mm} \implies
+$\forall \texttt{m1}.\, \{True \land True\hspace{3mm} \implies
 \exists \texttt{m2}. \\
@@
 
-$\forall \texttt{m1}. \exists \texttt{m2}.
+$\forall \texttt{m1}. \exists \texttt{m2}.\,
 (\texttt{p-send(m1)} = \texttt{p-send(m2)}

### 2020-09-08 2016-Weak-FH-Bisim/WeakBisim.tex
derniere passe ?

--- 2020-09-07 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 Figure \ref{SimpleProt:Impl} shows the pNet model of the protocol implementation.
-When the $\symb{Medium}$ detects an error (modelled by a local $\tau$ action), it sends back a $\texttt{m\_error}$ message to the $\symb{Sender}$.
+When the $\symb{Medium}$ detects an error (modelled by a local $\tau$ action), it sends back a $\texttt{m-error}$ message to the $\symb{Sender}$.
 The $\symb{Sender}$ increments its local error counter $ec$, and resends the message (including $ec$) to the $\symb{Medium}$, that will, eventually, transmit $m,ec$ to the $\symb{Receiver}$.
@@
 
-  \begin{example}[A weak open automaton]
+  \begin{example}[Weak open automata]
     Figures \ref{SimpleProtCounter:WeakSpecOA} and \ref{SimpleProtCounter:ImplWOA2} respectively show the weak automata of the simple protocol specification and implementation.
@@
 $ WI_1 = \openrule
-{\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], ()}
+{\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{x}. \texttt{p-a} \neq \texttt{p-send(x)} ], ()}
 {s \OTWeakarrow {\texttt{p-a}} s}
@@
 \end{mathpar}
- there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
+ there exist weak open transitions $\symb{WOT}_x^{\;x\in X} \subseteq \WT_2$:
  \begin{mathpar}
@@
 We have developed tool support for computing the
-symbolic semantics in term of open-automata \cite{QBMZ-AVOCS18}, and have
+symbolic semantics in term of open automata \cite{QBMZ-AVOCS18}, and have
 developed algorithms to check strong FH-bisimulation \cite{hou:hal-02406098}.  
@@
 \label{lem-rel-OT-WOT} Let $A = \mylangle J,\mathcal{S}, s_0,V_1,
-    \mathcal{T}\myrangle$ be open automata and $\mylangle J,\mathcal{S}, s_0,V_2,
+    \mathcal{T}\myrangle$ be an open automaton and $\mylangle J,\mathcal{S}, s_0,V_2,
     \WT\myrangle$ be the
-weak open automata derived from $A$.  The two following statements are equivalent
+weak open automaton derived from $A$.  The two following statements are equivalent
 %For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
@@
     \WT_1\myrangle$ and $\mylangle J,\mathcal{S}_2,t_0, V_2, \WT_2\myrangle$ be the
-weak open automata derived from $A_1$ and $A_2$ respectively.
+weak open automaton derived from $A_1$ and $A_2$ respectively.
 For any  states
@@
 $ WI_1 = \openrule
-{\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], ()}
+{\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{x}. \texttt{p-a} \neq \texttt{p-send(x)} ], ()}
 {S \OTWeakarrow {\texttt{p-a}} S}$
@@
 $ WI_2 = \openrule
-{\{\texttt{Q}\mapsto \texttt{q-b}\}, [\forall \texttt{m,ec}. \texttt{q-b} \neq \texttt{q-recv(m,ec)} ], ()}
+{\{\texttt{Q}\mapsto \texttt{q-b}\}, [\forall \texttt{x,y}. \texttt{q-b} \neq \texttt{q-recv(x,y)} ], ()}
 {S \OTWeakarrow {\texttt{q-b}} S}$
@@
 $ WI_4P(n) = \openrule
-         {\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], \\
+         {\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{x}. \texttt{p-a} \neq \texttt{p-send(x)} ], \\
    (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec}+n, \texttt{s\_ec}\gets \texttt{s\_ec}+n)}
@@
 $ WI_4Q(n) = \openrule
-         {\{\texttt{Q}\mapsto \texttt{q-b}\}, [\forall \texttt{m,ec}. \texttt{q-b} \neq \texttt{q-recv(m,ec)} ],\\
+         {\{\texttt{Q}\mapsto \texttt{q-b}\}, [\forall \texttt{x,y}. \texttt{q-b} \neq \texttt{q-recv(x,y)} ],\\
    (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec}+n, \texttt{s\_ec}\gets \texttt{s\_ec}+n)}
@@
 $ WI_{456*}P(n) = \openrule
-        {\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], 
+        {\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{x}. \texttt{p-a} \neq \texttt{p-send(x)} ], 
     (\texttt{s\_msg}\gets \texttt{s\_msg}, \texttt{s\_ec}\gets \texttt{s\_ec}+n)}
@@
          Note: if we were using the alternative Weak bisim from Appendix \ref{app-WFH-equiv}, Lemma \ref{lem-rel-OT-WOT}, that is checking strong bisimulation between the corresponding 
-weak automata, we would have a more transitions coverage to examine, as we have 4 weak transitions for $b0$ in the specification weak automaton, and 7 WOTs (including 4 
+weak automaton, we would have a more transitions coverage to examine, as we have 4 weak transitions for $b0$ in the specification weak automaton, and 7 WOTs (including 4 
 parameterized WOTs) from 000 in the implementation automaton.

### 2020-09-08 2016-Weak-FH-Bisim/WeakBisim.tex
pb de merge ?
qq overful

--- 2020-09-08 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
-\documentclass{lmcs}
-
+\documentclass[draft]{lmcs}
+\overfullrule=1mm
 \usepackage[T1]{fontenc}
@@
 \item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
-  synchronisation vectors. $\forall k\!\in\! K.\,
+  synchronisation vectors. $\forall k\!\in\! K,
   \symb{SV}_k\!=\!\SV{\alpha_{l}^{l\in I_k \uplus J_k}}{\alpha'_k}{e_k}$ where
@@
 \end{mathpar}
- such that  $\forall x.\, J'=J_{x}$ and there exists $\Pred_{s',t_x}$ such that $(s',t_x|\Pred_{s',t_x})\in 
+ such that  $\forall x, J'=J_{x}$ and there exists $\Pred_{s',t_x}$ such that $(s',t_x|\Pred_{s',t_x})\in 
  \mathcal{R}$
@@
 			(\texttt{b\_ec}\gets \texttt{b\_ec}+1) }
-         {\texttt{b1}\OTWeakarrow \tau \texttt{b1}}$; $\openrule
+         {\text{b1}\OTWeakarrow \tau \text{b1}}$; $\openrule
          {\{\}, True,
 			(\texttt{b\_ec}\gets \texttt{b\_ec}+1) }
-         {\texttt{b1} \OTWeakarrow \tau \texttt{b1}}$;  $\openrule
+         {\text{b1} \OTWeakarrow \tau \text{b1}}$;  $\openrule
          {\{\}, True,
 			() }
-         {\texttt{b1} \OTWeakarrow \tau \texttt{b1}}$. Then Rule \WTTrois~ produces  $\openrule
+         {\text{b1} \OTWeakarrow \tau \text{b1}}$. Then Rule \WTTrois~ produces  $\openrule
          {\{\}, True,
 			(\texttt{b\_ec}\gets \texttt{b\_ec}+2) }
-         {\texttt{b1} \OTWeakarrow \tau \texttt{b1}}$. We can iterate this construction an arbitrary number of times, getting for any natural number $n$ a weak open transition:
+         {\text{b1} \OTWeakarrow \tau \text{b1}}$. We can iterate this construction an arbitrary number of times, getting for any natural number $n$ a weak open transition:
   $\openrule
@@
 			(\texttt{ec}\gets \texttt{ec}+n) }
-        {\texttt{b1} \OTWeakarrow \tau \texttt{b1}}\, \forall n \geq 0$.
+        {\text{b1} \OTWeakarrow \tau \text{b1}}\, \forall n \geq 0$.
 Finally,  applying again \WTTrois, and using the central open transition having \texttt{\nounderline{out(b\_msg,b\_ec)}}  as $\alpha$, we get the resulting weak open transition between b1 and b0 (as shown in Figure \ref{WOT2}).
@@
 
-$ \forall n\ge 0.\, WI_3(n) = \openrule
+$ \forall n\ge 0. WI_3(n) = \openrule
   {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
@@
 
-$  \forall n\ge 0.\, WI_4(n) = \openrule
+$  \forall n\ge 0. WI_4(n) = \openrule
          {\{\}, True, 
@@
 
-$  \forall n\ge 0.\, WI_{456}(n) = \openrule
+$  \forall n\ge 0. WI_{456}(n) = \openrule
          {\{\}, True, 
@@
 
-$ \forall n\ge 0.\, WI_{6a}(n) = \openrule
+$ \forall n\ge 0. WI_{6a}(n) = \openrule
          {\{\}, True, 
@@
       \begin{multline*}
-\forall fv_{OT}.\, \Big\{ \Pred \land \Pred_{OT} \implies\\
+\forall fv_{OT}. \Big\{ \Pred \land \Pred_{OT} \implies\\
  \bigvee_{x\in X}\!
@@
   \item The verification condition \\
-    $\forall fv_{OT}.\, \{ \Pred \land \Pred_{OT}\\
+    $\forall fv_{OT}. \{ \Pred \land \Pred_{OT}\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
@@
      \!\land\! \alpha\!=\!\alpha_x\! \land\!  
-     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)\right]\}}$
+     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\!\Post_{OT_x}}\right)\right]\}}$
 
@@
 
-$\forall \texttt{m1}.\, \{True \land True\hspace{3mm} \implies
+$\forall \texttt{m1}. \{True \land True\hspace{3mm} \implies
 \exists \texttt{m2}. \\
@@
 
-$\forall \texttt{m1}. \exists \texttt{m2}.\,
+$\forall \texttt{m1}. \exists \texttt{m2}.
 (\texttt{p-send(m1)} = \texttt{p-send(m2)}
@@
 
-We are currently extending this work,  looking at  both further properties of FH-bisimulation, but also
+We are currently extending this work,  looking at further properties of FH-bisimulation, but also
 the relations with existing equivalences on both closed and open systems. In particular, our model being significantly different from those considered in \cite{IngolfsdottirL:2001}, it
@@
 
-       	This is verified for each $p\in P$. Overall,  we have a family of open 
+       	This is verified for each $p\in P$.\\ Overall,  we have a family of open 
        	transitions 
@@
 
- \subsection{Proof of Theorem ~\ref{thm-congr-eq}}
+ \subsection{Proof of Theorem ~\ref{thm-congr-eq}}~\\
 \noindent{\bf  Congruence}:
@@
  	does not   	change the validity of the formula (those variables are not used).
+\fussy
  	\item Concerning the last term, we need 
@@
  	and thus the substitution $\subst{Post\,'}$ has no effect on it.
+\sloppy
  \end{itemize}	
@@
 				 } {s' \OTWeakarrow {\tau} s'}\! \in\! \WT
-\\
+\\\\
 \set{\gamma''}= \vis{\set{\beta_{10}}} \dotcup \set{\gamma}\subst{\Post_{10}}\\
-\Pred\,''=\Pred_{10}\land\Pred\subst{\Post_{10}}\\%\land (\Pred_3\subst{\Post_2})\subst{\Post_{10}}
+\Pred\,''\!=\!\Pred_{10}\land\Pred\subst{\Post_{10}}\\\\%\land (\Pred_3\subst{\Post_2})\subst{\Post_{10}}
 \Post\,''=\Id(s'')\shortotimes\Post\shortotimes\Post_{10} \\ \alpha''=\alpha'\subst{\Post_{10}}
@@
    \underbrace{\Pred_{OT_a}\land\Pred_{OT_{b}} \subst{\Post_{OT_a}} \land 
-  \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}}_{\Pred} \land  \underbrace{\alpha'\subst{\Post_1}}_{\alpha}=\underbrace{\alpha_{2 b} \subst{\Post_{OT_a}}}_{\alpha''} \land\\ \Pred_{s_{31},c}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{c}}\shortotimes \Post_{OT_{b}}\shortotimes\Post_{OT_a}}_{\Post}})
+  \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}}_{\Pred} \land  \underbrace{\alpha'\subst{\Post_1}}_{\alpha}=\underbrace{\alpha_{2 b} \subst{\Post_{OT_a}}}_{\alpha''} \\\land \Pred_{s_{31},c}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{c}}\shortotimes \Post_{OT_{b}}\shortotimes\Post_{OT_a}}_{\Post}})
 \end{multline*}

### 2020-09-08 2016-Weak-FH-Bisim/WeakBisim.tex

--- 2020-09-08 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 This modification is required to manage in a finite way all possible instantiations of an OT.
-In the case of weak FH-Bisimulation, the proof obligation from definition \ref{def-Weak-bisim} becomes:
+In the case of weak FH-Bisimulation, the proof obligation from Definition \ref{def-Weak-bisim} becomes:
       \begin{multline*}
@@
 {e_b}\in \set{\symb{SV}}\right), %&
-\forall i\in I'\cap J,\, \alpha_i=\tau \implies %\\
+\forall i\in I'\cap J.\, \alpha_i=\tau \implies %\\
 %& 

### 2020-09-08 2016-Weak-FH-Bisim/Coverletter.tex

@@
 
+\smallskip
+
+Finally, after a brief exchange with Alexandra Silva, we improved the form of the paper as follows.
+We improved the spacings here and there (e.g.
+between subscripts and rest of text) and tracked overfull boxes.
+We also adopted a reduced number of symbols and tried to reduce the use of $<....>$ to the synchronisation vectors where this notation is usual now.
+
 \begin{flushright}

### 2020-09-08 2016-Weak-FH-Bisim/Coverletter.tex
cover + overfull again
typos, and two "todos"...

@@
                       {\end{alltt}}
-
+\usepackage{color}
+\newcommand{\Eric}[1]{\textcolor{blue}{#1}}
 \thispagestyle{empty}
@@
 This theory is based on the definition of operators as open processes.
-We define the operational semantics of open processes, using open transitions that include symbolic hypotheses on the behaviour of the holes.The  semantics of pNets is given by means of a symbolic open transition system.
+We define the operational semantics of open processes, using open transitions that include symbolic hypotheses on the behaviour of the holes.
+The  semantics of pNets is given by means of a symbolic open transition system.
 Behavioural equivalences for pNets, like strong and weak bisimilarities, are defined over such a open transition systems.
-We finally prove that these equivalences are compositional.
+We finally prove that these equivalences are c
+ompositional.
 
@@
 We think this article fits with the scope and criteria of ``Logical Methods in Computer Science'' for the following reasons.
-First, to our knowledge this is the first paper we propose a theoretical framework for analysing the behaviour of open systems modelled as pNets, i.e., open terms of suitable process calculi.
+First, to our knowledge this is the first paper proposing a theoretical framework for analysing the behaviour of open systems modeled as pNets, i.e., open terms of suitable process calculi.
 Second, the quite theoretical and fundamental approach adopted in this paper fits well to the topics of LMCS.
@@
 The theory is based on the definition of operators as open pNets.
-However, the study of compositionability was only partial, and in particular the proof that bisimulation is an equivalence that is one new contribution of this article.
+However, the study of compositionability was only partial, and in particular the proof that bisimulation is an equivalence that is one of the new contributions of this article.
 Additionally, previous works only formalised strong bisimulation, and the formalisation and proofs dealing with weak bisimulation are also new here.
@@
 keep the two first appendices in the final version of the paper (leading to a
-paper of 73 pages) because they are important to understand the paper.
-The other appendices will be available as a research report, we keep
+paper of 73 pages) \Eric{if we keep A and B, we get 66 pages} because they are important to understand the paper.
+The other appendices \Eric{there is only one left out in that case.
+So siingular.
+Did we change the structure of appendices ?
+Do you really intend to keep both A and B ?} will be available as a research report, we keep
 them in the submission to ease the work of the reviewers. 

### 2020-09-11 2016-Weak-FH-Bisim/Coverletter.tex
coverletter et .pdf

@@
 keep the two first appendices in the final version of the paper (leading to a
-paper of 73 pages) \Eric{if we keep A and B, we get 66 pages} because they are important to understand the paper.
-The other appendices \Eric{there is only one left out in that case.
-So siingular.
-Did we change the structure of appendices ?
-Do you really intend to keep both A and B ?} will be available as a research report, we keep
+paper of 66 pages)  because they are important to understand the paper and contain the proofs.
+The other appendix  will be available as a research report, we keep
 them in the submission to ease the work of the reviewers. 
-Of course, depending on the opinion of the reviewers, we could also move more material to  the body of the paper, or remove more proofs from the published version and only keep them in the report.
+Of course, depending on the opinion of the reviewers, we could also move more material to  the body of the paper, or remove more proofs from the published version and only keep them in the report for example.
 
@@
 Finally, after a brief exchange with Alexandra Silva, we improved the form of the paper as follows.
-We improved the spacings here and there (e.g.
-between subscripts and rest of text) and tracked overfull boxes.
+We improved the spacings at some places (e.g.
+between superscripts and rest of text) and tracked overfull boxes.
 We also adopted a reduced number of symbols and tried to reduce the use of $<....>$ to the synchronisation vectors where this notation is usual now.

### 2020-09-12 2016-Weak-FH-Bisim/WeakBisim.tex
cover + overfull again
coverletter et .pdf
coherence listings de annexe C

@@
 
-\documentclass[draft]{lmcs}
-\overfullrule=1mm
+\documentclass{lmcs}
+%\overfullrule=1mm
 \usepackage[T1]{fontenc}
@@
 %\date{}                                           % Activate to display a given date or no date
-\author{Rab\'ea Ameur-Boulifa}
-\address{LTCI, T\'el\'ecom Paris, Institut Polytechnique de Paris, France
-}         
-\email{rabea.ameur-boulifa@telecom-paris.fr}                % Activate to display a given date or no date
 
@@
 \begin{figure}[t]
-   \includegraphics[width=.37\textwidth]{XFIG/SimpleProt-Schema}
-   \includegraphics[width=.62\textwidth]{XFIG/SimpleProt2-Spec}
+   \includegraphics[width=.37\textwidth]{XFIG/SimpleProt-Schema.pdf}
+   \includegraphics[width=.62\textwidth]{XFIG/SimpleProt2-Spec.pdf}
    \caption{pNet structure of the example and specification expressed as a pNet}
@@
 \begin{minipage}{0.30\linewidth}
-	\includegraphics[width=\linewidth]{XFIG/Bisim}
+	\includegraphics[width=\linewidth]{XFIG/Bisim.pdf}
 \end{minipage}
@@
  and  \\
-$\Pred_{s,t} \land \Pred_{OT}\!\implies\!
+$\Pred_{s,t} \land \Pred_{OT}\!\!\implies\!\!\!
 \displaystyle{\bigvee_{x\in X}
@@
 
+\fussy
 %\begin
@@
 %\end{theorem}
+\sloppy
 
@@
 \alpha_Q=&\alpha'_Q\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}\\
-\set{\gamma}=&\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{j=h-1}^{0}\!\! \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=k}^{0}\Post_{1j}}} \dotcup%\\
+\set{\gamma}=&\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\!\!\bigotimes_{j=h-1}^{0}\!\! \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=k}^{0}\!\!\Post_{1j}}} \dotcup%\\
 		%&
- \mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{j=h-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=k}^{0}\Post_{1j}} }\\
-\Pred_Q=&\bigwedge_{h=0}^{k}\!\Pred_{1h}\subst{\!\bigotimes_{j=h-1}^{0}\!\!\!\Post_{1 j}}\land \Pred_2\subst{\bigotimes_{h=k}^{0}\!\Post_{1h}}\land%\\
+ \mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\!\!\bigotimes_{j=h-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=k}^{0}\Post_{1j}} }\\
+\Pred_Q=&\bigwedge_{h=0}^{k}\!\Pred_{1h}\subst{\!\!\bigotimes_{j=h-1}^{0}\!\!\!\!\Post_{1 j}}\land \Pred_2\subst{\bigotimes_{h=k}^{0}\Post_{1h}}\land%\\
 %&
@@
 \begin{align*}
-\gamma_{j_0}=&~[\beta_0..\beta_n]\\
+\gamma_{j_0}\!=&~[\beta_0..\beta_n]\\
  =&\!\!
 {\mybigdotcup_{\substack{i=0\\j_0\in J_{1i}}}^{m_1}\!\!\!
-\vis{{\beta_{1ij_0}}\subst{\!\bigotimes_{k=i-1}^{0} \!\!\!\Post_{1k} } }  \,\dotcup\, \vis{{\beta_{2j_0}}\subst{\!\bigotimes_{k=m_1}^{0}\!\!\Post_{1k}}}}\dotcup %\\
+\vis{{\beta_{1ij_0}}\subst{\!\bigotimes_{k=i-1}^{0} \!\!\!\!\Post_{1k} } }  \,\dotcup\, \vis{{\beta_{2j_0}}\subst{\!\bigotimes_{k=m_1}^{0}\!\!\!\Post_{1k}}}}\dotcup\!
+%\\
 %&
 { \!\mybigdotcup_{\substack{i=0\\j_0\in J_{3i}}}^{m_2}\!\! \vis{{\beta_{3ij_0}} \subst{\!\bigotimes_{k=i-1}^{0}\!\!\!\Post_{3k}\shortotimes\Post_2\shortotimes
-\!\bigotimes_{k=m_1}^{0}\!\!\Post_{1k}}}}
+\!\!\bigotimes_{k=m_1}^{0}\!\!\!\Post_{1k}}}}
 \end{align*}}
@@
 \begin{split}\gamma'_j=&\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}}\subst{\bigotimes_{k=i-1}^{0}\! \Post_{1k} } }  \dotcup  \vis{{\beta_{2j}}\subst{\bigotimes_{k=m_1}^{0}\!\Post_{1k}}}\, \dotcup
-\mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}
+\mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij} \subst{\!\bigotimes_{k=i-1}^{0}\!\!\!\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\!\!\Post_{1k}}}
 \end{split}
@@
 \begin{align*}
-\Pred\,''&=\Big(\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land%\\ &\qquad
+\Pred\,''&=\Big(\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}\land%\\ &\qquad
 %~\quad
-\bigwedge_{i=0}^{m_3}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\Post\,'_{1j}}\Big)\\
+\bigwedge_{i=0}^{m_3}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\Post\,'_{1j}}\Big)\\
 &=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}\land\Pred_2\subst{\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\Big)\\&\qquad
-\land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i%\\&\qquad
-\land \Big( \bigwedge_{i=0}^{m-1}(\beta_{1{n_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j={n_i}-1}^{0}\Post\,'_{1j}}\land(\beta_{2{j_0}}=\alpha_m) \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\ &\qquad
-~\quad\bigwedge_{i=m+1}^{n}(\beta_{3{n'_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j=n'_i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\Big)\displaybreak[0]\\
+\land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\!\!\Post_i%\\&\qquad
+\land \Big( \bigwedge_{i=0}^{m-1}(\beta_{1{n_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j={n_i}-1}^{0}\Post\,'_{1j}}\land(\beta_{2{j_0}}=\alpha_m) \subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}\land\\ &\qquad
+~\quad\bigwedge_{i=m+1}^{n}(\beta_{3{n'_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j=n'_i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}\Big)\displaybreak[0]\\
 &=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}\big)\land\Pred_2\subst{\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\Big)\\&\qquad
-\land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i
-\land \Big(\bigwedge_{i=0}^{m-1}(\beta_{i}=\alpha_i)\subst{\bigotimes_{j={i-1}}^{0}\Post_{j}}\land(\beta_m=\alpha_m )\subst{\bigotimes_{j=m}^{0}\Post_{j}}\land\\ &\qquad
-~\quad\bigwedge_{i=m+1}^{n}(\beta_i=\alpha_i)\subst{\bigotimes_{j=i-1}^{m}\Post_j\shortotimes\Post_m\shortotimes\bigotimes_{j=m-1}^{0}\Post_{j}}\Big)\\
+\land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\!\!\Post_i
+\land \Big(\bigwedge_{i=0}^{m-1}(\beta_{i}=\alpha_i)\subst{\bigotimes_{j={i-1}}^{0}\!\!\Post_{j}}\land(\beta_m=\alpha_m )\subst{\bigotimes_{j=m}^{0}\Post_{j}}\land\\ &\qquad
+~\quad\bigwedge_{i=m+1}^{n}(\beta_i=\alpha_i)\subst{\bigotimes_{j=i-1}^{m}\!\!\Post_j\shortotimes\Post_m\shortotimes\bigotimes_{j=m-1}^{0}\!\!\Post_{j}}\Big)\\
 &=\Pred
@@
 
-The first piece of code is the textual definition of the SimpleProtSpec
-pNet, that was drawn in Figure \ref{SimpleProt:Impl}, page \pageref{SimpleProt:Impl}. This code should be intuitive enough to read, with the following
-conventions, that brings some user-friendly features that are mapped by the editor into pure pNet constructs.
+The first piece of code is the textual definition of the SimpleSystemSpec
+pNet (named SimpleProtSpec2 in the code), that was drawn in Figure \ref{SimpleProt:Impl}, page \pageref{SimpleProt:Impl}. This code should be intuitive enough to read, with the following
+language conventions, that brings some user-friendly features, mapped by the editor into pure pNet constructs.
 
@@
     ``const''. They are used either as functions with argument, as
-    typically \texttt{in(msg)}, or constants without argument, denoted
-    as \texttt{\$tau}. Identifiers without the ``\$'' marker are
-    variables.
-  \item Variables can be declared as global variables of a pLTS (e.g. \texttt{m\_msg} in \texttt{M1}), or a pNet Node in the case of synchronisation vector variables (e.g. \texttt{p\_a}),
-    or as input variables in a pLTS, as \texttt{?msg} in \texttt{M1}.
-  \item The variables in the guards of synchronisation vectors do not need to be explicitly quantified: by convention, all variables in a guard that do not appear inside the vector actions will be recognised as bound by a \emph{forall} quantifier inside the guard.
-    \item The tools will check that everything is correctly declared, and that variables are used properly and do not conflict between different objects, that vectors have coherent length, etc.
+    typically \texttt{in(msg)}, or constants without argument, typically as "tau()".
+  \item Variables can be declared as global variables of a pLTS (e.g. \texttt{m\_msg} in \texttt{PerfectBuffer}), or a pNet Node in the case of synchronisation vector variables (e.g. \texttt{p\_a}),
+    or as input variables in a pLTS, as \texttt{?msg} in \texttt{PerfectBuffer}.
+  \item The variables in the guards of synchronisation vectors (e.g.
+in SV1) do not need to be explicitly quantified: by convention, all variables in a guard that do not appear inside the vector actions will be recognised as bound by a \emph{forall} quantifier inside the guard.
+    \item The tools will check that everything is correctly declared, that variables are used properly and do not conflict between different objects, that vectors have coherent length, etc.
 \end{itemize}
@@
 
-pLTS M1
-initial a0 
-vars ?msg:Data
-vars m_msg:Data m_ec:Int
-
-state a0
-transition in(msg) -> a1 {m_msg:=msg, m_ec:=0}
-
-state a1
-transition out(m_msg, m_ec) -> a0
-transition synchro($tau)  -> a1 {m_ec:=m_ec+1}
+pLTS PerfectBuffer
+initial b0 
+vars ?m:Data
+vars b_msg:Data b_ec:Nat
+
+state b0
+transition in(m) -> b1 {b_msg:=m, b_ec:=0}
+
+state b1
+transition out(b_msg, b_ec) -> a0
+transition synchro(tau())  -> b1 {b_ec:=b_ec+1}
 
@@
 holes P,Q
-subnets P,M1,Q
-vars p_a,q_a:Action m:Data ec:Int
+subnets P,PerfectBuffer,Q
+vars p_a,q_b:Action m:Data ec:Nat
 
 vector SV0 <p_send(m), in(m),_>->synchro(in(m))
-vector SV1 <p_a,_,_>->p_a [p_a != p_send(m)]
-vector SV2 <_, out(m,ec), q_recv(m)>->synchro(out(m,ec))
-vector SV3 <_,_,q_a>->q_a [q_a != q_recv(m)]
+vector SV1 <p_a,_,_>->p_a [p_a != p_send(x)]
+vector SV2 <_, out(m,ec), q_recv(m,ec)>->synchro(out(m,ec))
+vector SV3 <_,_,q_b>->q_a [q_b != q_recv(x,y)]
 
@@
 
-Next is the code for the SimpleProtImpl pNet:
+Next is the code for the SimpleSystem implementation pNet (named SimpleProtImpl2):
 \medskip
@@
 
-pLTS M1
-  initial a0
-  vars ?msg:Data ?c:Int
-  vars m_msg:Data m_ec:Int
-state m0
-  transition m_recv(msg,c) -> m1 {m_msg:=msg, m_ec:=c}
-state m1
-  transition m_send(m_msg, m_ec) -> m0 
-  transition synchro($tau) -> m2
-state m2
-  transition $m_error -> m0
-
 pLTS Sender
   initial s0
-  vars ?msg:Data
-  vars  s_msg:Data s_ec:Int
+  vars ?m:Data
+  vars  s_msg:Data s_ec:Nat
 state s0
-  transition s_recv(msg) -> s1 {s_msg:=msg, s_ec:=0}
+  transition s_recv(m) -> s1 {s_msg:=m, s_ec:=0}
 state s1
@@
 state s2
-  transition $s_ack -> s0
-  transition $s_error -> s1 {s_ec:=s_ec+1}
+  transition s_ack() -> s0
+  transition s_error() -> s1 {s_ec:=s_ec+1}
+
+pLTS Medium
+  initial m0
+  vars ?m:Data ?ec:Nat
+  vars m_msg:Data m_ec:Nat
+state m0
+  transition m_recv(m,ec) -> m1 {m_msg:=m, m_ec:=ec}
+state m1
+  transition m_send(m_msg, m_ec) -> m0 
+  transition synchro(tau()) -> m2
+state m2
+  transition m_error() -> m0
 
@@
   initial r0
-  vars ?msg:Data ?c:Int
-  vars r_msg:Data r_ec:Int
+  vars ?m:Data ?ec:Nat
+  vars r_msg:Data r_ec:Nat
 state r0
-  transition r_recv(msg,c) -> r1 {r_msg:=msg, r_ec:=c}
+  transition r_recv(m,ec) -> r1 {r_msg:=msg, r_ec:=ec}
 state r1
@@
 state r2
-  transition $r_ack -> r0
+  transition r_ack() -> r0
 
 pNet medium
-  subnets Sender, M1, Receiver
-  vars m:Data c:Int
+  subnets Sender, Medium, Receiver
+  vars m:Data c:Nat
 vector SV0 <s_recv(m), _, _>->in(m)
-vector SV1 <s_send(m,c), m_recv(m,c), _>->synchro($tau)
-vector SV2 <_, m_send(m,c), r_recv(m,c)>->synchro($tau)
-vector SV3 <$s_ack, _, $r_ack>->synchro($tau)
-vector SV4 <$s_error, $m_error, _>->synchro($tau)
-vector SV5 <_, _, r_send(m,c)>->out(m,c)
+vector SV1 <s_send(m,ec), m_recv(m,ec), _>->synchro(tau())
+vector SV2 <_, m_send(m,ec), r_recv(m,ec)>->synchro(tau())
+vector SV3 <s_ack(), _, r_ack()>->synchro(tau())
+vector SV4 <s_error(), m_error(), _>->synchro(tau())
+vector SV5 <_, _, r_send(m,ec)>->out(m,ec)
 
@@
   subnets P,medium,Q
-  vars p_a,q_a:Action  m:Data c:Int
+  vars p_a,q_a:Action  m:Data c:Nat
 vector SV0 <p_send(m), in(m),_>->synchro(in(m))
-vector SV1 <p_a,_,_>->p_a [p_a != p_send(m)]
-vector SV2 <_, out(m,c), q_recv(m,c)>->synchro(out(m,c))
-vector SV3 <_,_,q_a>->q_a [q_a != q_recv(m,c)]
+vector SV1 <p_a,_,_>->p_a [p_a != p_send(x)]
+vector SV2 <_, out(m,ec), q_recv(m,ec)>->synchro(out(m,ec))
+vector SV3 <_,_,q_b>->q_b [q_b != q_recv(x,y)]
 \end{lstlisting}
@@
 
-All the following transitions are parametrized by an integer $n\in \mathcal{N}$, meaning they stand for the corresponding (infinite) set of weak OTs. 
+All the following transitions are parameterised by an integer $n\in \mathcal{N}$, meaning they stand for the corresponding (infinite) set of weak OTs. 
 In some cases, this set is further restricted (see e.g. $WI_{7b}(n)$), in which cases we have added an explicit quantifier.
@@
 
-\begin{tabular}{|l|l|c|}
+\noindent\begin{tabular}{|@{\,}l@{\,}|@{\,}l@{\,}|@{\,}c@{\,}|}
 \hline
-    WOT name & Pairs of source states and target states & \# of WOTs \\
+    WOT name & Pairs of source states and target states & \# WOTs \\
     \hline
@@
 weak automaton, we would have a more transitions coverage to examine, as we have 4 weak transitions for $b0$ in the specification weak automaton, and 7 WOTs (including 4 
-parameterized WOTs) from 000 in the implementation automaton.
+parameterised WOTs) from 000 in the implementation automaton.
 
@@
     $\forall fv_{OT}. \{ \Pred \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!\!
    \left[\exists fv_{OT_x}.
@@
      \!\land\! \alpha\!=\!\alpha_x\! \land\!  
-     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)\right]\}}$
+     \Pred_{s',t_x}\subst{\Post_{OT}\!\uplus\!\Post_{OT_x}}\right)\right]\}}$
 
@@
 
+\end{document}
   \subsection{Test}
@@
   $\left< 1,2,3 \right>$
-
-\end{document}

### 2020-09-14 2016-Weak-FH-Bisim/WeakBisim.tex
coherence Fig2 - code

@@
 As we have seen above, the effect of rule $WT_3$ when a silent action have an effect on the variable $ec$ will generate an infinite family of WOTs, depending on the number of iterations through the loops.
-We denote these families using a "meta-variable" $n$, ranging over $\mathcal{N}$.
+We denote these families using a "meta-variable" $n$, ranging over $\texttt{Nat}$.
 % \TODO{Qu'est-ce qu'on avait dit ici pour "$n$" ? a droite ou a gauche, mais pas les deux ?Et est-ce qu'on le laisse en italique dans les expressions, pour souligner son statut de parametre ?.
@@
 The first piece of code is the textual definition of the SimpleSystemSpec
-pNet (named SimpleProtSpec2 in the code), that was drawn in Figure \ref{SimpleProt:Impl}, page \pageref{SimpleProt:Impl}. This code should be intuitive enough to read, with the following
+pNet (named SimpleProtSpec2 in the code here), that was drawn in Figure \ref{SimpleProt:Impl}, page \pageref{SimpleProt:Impl}. This code should be intuitive enough to read, with the following
 language conventions, that brings some user-friendly features, mapped by the editor into pure pNet constructs.
@@
 
-vector SV0 <p_send(m), in(m),_>->synchro(in(m))
+vector SV0 <p_send(m),in(m),_>->synchro(in(m))
 vector SV1 <p_a,_,_>->p_a [p_a != p_send(x)]
-vector SV2 <_, out(m,ec), q_recv(m,ec)>->synchro(out(m,ec))
+vector SV2 <_,out(m,ec),q_recv(m,ec)>->synchro(out(m,ec))
 vector SV3 <_,_,q_b>->q_a [q_b != q_recv(x,y)]
@@
 
-pNet medium
-  subnets Sender, Medium, Receiver
+pNet SimpleProtocol
+  subnets Sender,Medium,Receiver
   vars m:Data c:Nat
-vector SV0 <s_recv(m), _, _>->in(m)
-vector SV1 <s_send(m,ec), m_recv(m,ec), _>->synchro(tau())
-vector SV2 <_, m_send(m,ec), r_recv(m,ec)>->synchro(tau())
-vector SV3 <s_ack(), _, r_ack()>->synchro(tau())
-vector SV4 <s_error(), m_error(), _>->synchro(tau())
-vector SV5 <_, _, r_send(m,ec)>->out(m,ec)
+vector SV0 <s_recv(m),_, _>->in(m)
+vector SV1 <s_send(m,ec),m_recv(m,ec),_>->synchro(tau())
+vector SV2 <_,m_send(m,ec),r_recv(m,ec)>->synchro(tau())
+vector SV3 <s_ack(),_,r_ack()>->synchro(tau())
+vector SV4 <s_error(),m_error(),_>->synchro(tau())
+vector SV5 <_,_,r_send(m,ec)>->out(m,ec)
 
@@
   holes P,Q
-  subnets P,medium,Q
+  subnets P,SimpleProtocol,Q
   vars p_a,q_a:Action  m:Data c:Nat
-vector SV0 <p_send(m), in(m),_>->synchro(in(m))
+vector SV0 <p_send(m),in(m),_>->synchro(in(m))
 vector SV1 <p_a,_,_>->p_a [p_a != p_send(x)]
-vector SV2 <_, out(m,ec), q_recv(m,ec)>->synchro(out(m,ec))
+vector SV2 <_,out(m,ec),q_recv(m,ec)>->synchro(out(m,ec))
 vector SV3 <_,_,q_b>->q_b [q_b != q_recv(x,y)]
@@
 
-All the following transitions are parameterised by an integer $n\in \mathcal{N}$, meaning they stand for the corresponding (infinite) set of weak OTs. 
+All the following transitions are parameterised by an integer $n\in \texttt{Nat}$, meaning they stand for the corresponding (infinite) set of weak OTs. 
 In some cases, this set is further restricted (see e.g. $WI_{7b}(n)$), in which cases we have added an explicit quantifier.

### 2020-10-16 2020-Newsemantics/WeakBisim.tex
cleaner semantics?

--- 2020-09-08 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
-\documentclass[draft]{lmcs}
-\overfullrule=1mm
+\documentclass[11pt]{article}
+%\overfullrule=1mm
 \usepackage[T1]{fontenc}
 \usepackage{lmodern}
+\usepackage{fullpage}
 %\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
@@
 
-\pagestyle{plain}
+%\pagestyle{plain}
 
@@
 
-\title{Compositional equivalences based on Open pNets
+\title{ Open pNets
 %\thanks{This work was partially funded by the Associated Team FM4CPS
@@
 }
-\author{Ludovic Henrio}
-\address{Univ Lyon, EnsL, UCBL, CNRS, Inria,  LIP, F-69342, LYON Cedex 07, France.}
-\email{ludovic.henrio@cnrs.fr}
-
-\author{Eric Madelaine}
-\address{INRIA Sophia Antipolis M\'edit\'erann\'ee, UCA, BP 93, 06902 Sophia Antipolis, France}
-\email{eric.madelaine@inria.fr}
-%\date{}                                           % Activate to display a given date or no date
-\author{Rab\'ea Ameur-Boulifa}
-\address{LTCI, T\'el\'ecom Paris, Institut Polytechnique de Paris, France
-}         
-\email{rabea.ameur-boulifa@telecom-paris.fr}                % Activate to display a given date or no date
-
-		%\section{}
-%\subsection{}
-
-\begin{abstract}
-
-Establishing equivalences between programs or system is crucial both for verifying correctness of programs, by establishing that two implementations are equivalent, and for justifying optimisations and program transformations, by establishing that a modified program is equivalent to the source one.
-There exist several equivalence relations for programs, and bisimulations are among the most versatile of these equivalences.
-Among bisimulation relations one distinguishes strong bisimulation, that requires that each action of a program is simulated by a single action of the equivalent program, a weak bisimulation that  is a coarser relations, allowing some of the actions to be
-  invisible or internal moves, and thus not simulated by the equivalent program.
-
-pNets is a generalisation of automata that includes parameters, and hierarchical composition.
-Open pNets are pNets with holes, i.e.
-placeholders inside the hierarchical structure  that can be filled by sub-systems.
-Reasoning on open pNets allows us to reason on open systems.
-  Open pNets have a notion of \emph{synchronised actions}
-  generalizing the usual internal actions (e.g. $\tau$ of CCS, or $i$
-  in Lotos).
-
-This article defines bisimulation relations  for the comparison of systems specified as pNets.
- We first define a strong bisimulation for open pNets.
-  In practice, as happens in process algebras, strong bisimulation is too strong, and
-  we need to define some coarser relations, taking into account
-  invisible or internal moves.
-  We then define an equivalence relation similar to
-  the classical \emph{weak bisimulation}, and study its properties.
-Among these properties we are interested in compositionality: If two systems are proven equivalent they will be undistinguishable by their context, and they will also be undistinguishable when their holes are filled with equivalent systems.
-The article is illustrated with a transport protocol running example; it shows the characteristics of our formalism and our bisimulation relations.
-\end{abstract}
 
@@
 % \tableofcontents
-
-\section{Introduction}
-
-In the nineties, several 
-works extended the basic behavioural models based on labelled
-transition systems to address value-passing or parameterised systems, using
-various symbolic encodings of the
-transitions~\cite{deSimone85,Larsen87}. 
-In \cite{IngolfsdottirL:2001,HennessyLin:TCS95}, Lin, Ingolfsdottir and Hennessy developed a full hierarchy of
-bisimulation equivalences, together with a proof system, for value passing CCS,
-including notions of symbolic behavioural semantics and various symbolic 
-bisimulations (early and late, strong and weak, and their congruent versions). They also extended this work to models with explicit assignments \cite{Linconcur96}.
-Separately J. Rathke~\cite{HennessyRathke:TCS98} defined another symbolic semantics for 
-a parameterised broadcast calculus, together with strong and weak bisimulation
-equivalences, and developed a symbolic model-checker based on a tableau
-method for these processes. 30 years later, no
-practical verification approach and no verification platform are
-using this kind of approaches to provide proof methods for
-value-passing processes or open process expressions.
-
-This article provides a theoretical background that allows us to implement such a verification 
-platform. We build upon the concept of pNets that allowed us to give a behavioural semantics 
-of distributed components and verify the correctness of distributed applications in the past 15 years. pNets  is a
-low level semantic framework for expressing the behaviour of various
-classes of distributed languages, and as a common internal format for
-our tools.  pNets allow the
-specification of parameterised hierarchical labelled
-transition systems:  labelled transition systems with parameters can be
-combined hierarchically.
-
-We develop here a semantics for a model of interacting processes with parameters and holes. 
-The main interest of our symbolic approach is to define a method to
-prove properties directly on open structures; these properties will then be preserved
-by any correct instantiation of the holes.
-As a consequence, our model allows us to reason on composition
-operators as well as on full-size distributed systems. The parametric
-nature of the model and the properties of compositionability of the
-equivalence relations are thus  the main
-strengths of  our approach.
-
-\subsubsection*{Previous Works and Contribution}
-While most of our previous works relied on closed, fully-instantiated semantics~\cite{BBCHM:article2008,AmeurBoulifa2017,HKM-FASE16}, it is only recently that we could design a first version of a  parameterised semantics for pNets with a strong bisimulation equivalence~\cite{henrio:Forte2016}.
-This article builds upon this previous parameterised semantics and provides a cleaner version of the semantics with a slightly simplified formalism.
-It also adds a notion of global state to automata.
-The slight simplification of the formalism allowed us to adopt a much cleaner presentation where the theory for open automata.
-The algebra used to define the semantics of pNets with holes, can be studied independently from its application to pNets.
-Also, in \cite{henrio:Forte2016} the study of compositionability was only partial, and in particular the proof that bisimulation is an equivalence is one new contribution of this article and provides a particularly interesting insight on the semantic model we use.
-The new formalism allowed us to extend the work and define weak bisimulation  for open automata, which is entirely new.
-This allows us to define a weak bisimulation equivalence for open pNets with valuable properties of compositionality.
-To summarise, the contribution of this paper are the following:
-\begin{itemize}
-\item The definition of open automata: an algebra of parameterised automata with holes, and a strong bisimulation equivalence.
-This is an adaptation of~\cite{henrio:Forte2016} with an additional property stating that strong bisimulation equivalence is indeed an equivalence relation.
-\item A semantics for open pNets expressed as translation to open automata. This is an adaptation of~\cite{henrio:Forte2016} with a complete proof that strong bisimulation is compositional.
-\item A theory of weak bisimulation for open automata, and its properties.
-It relies on the definition of weak open transitions that are derived from transitions of the open automaton by concatenating invisible action transitions with one (visible or not) action transition.
-The precise and sound definition of the concatenation is also a major contribution of this article.
-\item A resulting weak bisimulation equivalence for open pNets and a simple static condition on synchronisation vectors inside pNets that is sufficient to ensure that weak bisimulation is compositional.
-\item An illustrative example based on a simple transport protocol, showing the construction of the weak open transitions, and the proof of weak bisimulation.
-\end{itemize}
-
-\subsubsection*{Structure}
-This article is organised as follows. Section~\ref{sec:notations}
-provides the definition of pNets and introduces the notations used in
-this paper, including the definition of open pNets. 
-Section~\ref{sec:OT} defines open automata, i.e. automata
-with parameters and transitions conditioned by the behaviour of
-``holes''; a strong bisimulation equivalence for open automata is also
-presented in this section. 
-Section~\ref{section:op-semantics} gives
-the semantics of open pNets expressed as open automata, and states
-compositional properties on the strong bisimulation for open
-pNets. 
-Section~\ref{sec:weak} defines a weak bisimulation
-equivalence on open automata and derives weak bisimilarity for pNets,
-together with properties on compositionality of weak bisimulaiton for
-open pNets. 
-Finally, Section~\ref{sec:RW} discusses related works and Section~\ref{section:conclusion} concludes the
-paper.
 
@@
 we define the composition operation as follows:
-%\TODO{version d eric reprise et corrigee}
-%$(x_k\gets e_k)^{k\in K}\shortotimes \Post =  (x_k\gets e_k\subst{\Post})^{k\in K}$
-%\ERIC{J'ai un probleme ici... quand $Post'$ agit sur des vars de $t$ qui ne sont pas substitutees par $Post$, alors les 2 defs de $\shortotimes$ ci-dessus ne sont pas equivalentes:}\\
-%$F(x,z)(\subst{x\gets z}\shortotimes\subst{z\gets 1})=F(x,z)(\subst{x\gets 1})=F(1,z)$\\
-%\ERIC{Alors que}\\
-%$(F(x,z)\subst{x\gets z})\subst{z\gets 1})=F(z,z)\subst{z\gets 1}=F(1,1)$
-%
-%\ERIC{Une definition plus correcte serait peut-etre:}\\
 
@@
 where $K''=\{k'\in K'|x'_{k'}\not\in\{x_k\}^{k\in K}\}$
-%
-%\LUDO{En fait comme on supose qu il y a pas de variable globale et donc que les post doivent affecter toutes les variables ce contre-exemple n est pas applicable!
-apres on peut definir comme ca si on veut ceinture et bretelles mais ca alourdit un peu la definitions}
-%
-%\ERIC{Heu Non... 
-%  En pratique, dans la composition de posts de la regle WT3, les posts assignent bien toutes les variables de leur OT (strong), mais dans la composition, on fini par avoir des trous...
-Voir page 21-22.
-On est tombes tous les deux separemment, Rabea et moi, sur ce genre de cas.}
-% 
-%\LUDO{euuh ca doit etre lie qu fait qu il manque des ec leftarrowec dans les selfloop de l'OA de spec.
-Plutot que changer la def et les preuves je propose de rajouter la condition $vars(s')=dom(Post)$ pour tous les OAs ce qui ne change rien a part pour les selfloop que l on s autorisait apparemment a ecrire en omettant $x:=x$ ...
-au pire l'identite est un post toujours correct et valide}
-
-\subsection{Parameterised Networks (pNets)}
+
+\section{A model of process composition}\label{sec:OT}
+
+The semantics of open pNets will be defined  as an open automaton. An open
+automaton is an automaton where each transition composes transitions of several LTSs with
+action of some holes, the transition occurs if some predicates hold, and can involve a 
+set of state modifications.
+This section defines open automata and a bisimulation theory for them.
+This section can be viewed as an improved version of the formalism described in \cite{henrio:Forte2016}, extending the automata with a notion of global variable, which makes the state of the automaton more explicit.
+We also adopt a semantics and logical interpretation of the automata that intuitively can be stated as follows: ``if a transition belongs to an open automaton, any refinement of this transition also belongs to the automaton''.
+
+\subsection{Open Automata}
+ Open automata (OA) are not composition structures but they are made of transitions that are dependent of the actions of the holes, and they can reason on a set of variables (potentially with only symbolic values).
+%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
+%different 
+%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
+\begin{definition}[Open transitions]\label{def:OT}
+	\label{def:OpenTransitions}
+	An \emph{open transition} (OT) over a
+	set $J$ of holes with sorts $\Sort_j^{j\in J}$, a set $V$ of variables, and a set of states $\mathcal{S}$ is 
+	a structure of the form:	
+	\begin{mathpar}
+	\openrule
+	{	\beta_j^{j\in J'}, \Pred, \phi}
+	{s \OTarrow {\alpha}s'}
+	\end{mathpar}
+	Where $J'\subseteq J$, $s, s'\in\mathcal{S}$ and $\beta_j$
+        is a transition of the hole $j$, with $\beta_j\in\Sort_j$. 
+Let $W$ be the set of variables in $V$ and all variables
+        in the different terms
+       $\beta_j$ and $\alpha$.
+$\alpha$ is an action 
+        label denoting the resulting action of this open transition.
+        \Pred\ is a predicate over the set of variables $W$.
+$\phi$, called \emph{effect} is a mapping from variables in $V$ to expressions over the set of variables $W$.
+$V$ is called the domain of the effect.
+ Open transitions are identified
+        modulo logical equivalence on their predicate. 
+\end{definition}
+
+It is important to understand the difference between the red dotted rule and a normal 
+inference rule. They correspond to two different logical levels.
+On one side, classical (black) inference rules  use  an expressive logic and are paper rules.
+ On the other side, open transition rules (with dotted lines) are logical implications, but using a simple logic (this logic includes the boolean expressions $\AlgB$, boolean operators, and term equality).
+   open transitions could typically be handled in a 
+ mechanised way.
+
+Suppose $V=x_i^{i\in [1..n]}$ then $\phi$ has the form $(x_i\to e_i)^{i\in [1..n]}$.
+
+Application of effect is as follows: $\phi(e)=(x_i\to e_i\subst{x_i\leftarrow e_i}$.
+
+Composition of effects over the same domain is as follows:
+Suppose $\phi=(x_i\to e_i)^{i\in [1..n]}$
+and
+$\psi=(x_i\to e'_i)^{i\in [1..n]}$.
+Then $\phi(x'_i\to e'_i)^{i\in [1..m]} =(x'_i\to e'_i\subst{x_i\leftarrow e'_i}^{i\in [1..n]})^{i\in [1..m]}$. That applies to states or effects.
+
+An open automaton is  an automaton where each transition is an open transition.
+\begin{definition}[Open automaton]
+	\label{def:open-automaton}
+	An \emph{open automaton} is a structure\\ $A =
+	\mylangle J,\mathcal{S},s_0,V,\mathcal{T}\myrangle$ where:
+	\begin{itemize}
+		\item[$\bullet$]   $J$ is a  set of indices.
+		\item[$\bullet$]   $\mathcal{S}$ is a set of states and $s_0$ an initial state
+		  among $\mathcal{S}$.
+ \item[$\bullet$] $V$ is a set of variables of the automaton
+		and each $v\in V$ may have an initial value $init(v)$.
+		\item[$\bullet$] $\mathcal{T}$ is a set of open transitions and for each
+		$t\in \mathcal{T}$ there exist  $J'$ with  $J'
+		\subseteq J$, such that $t$ is an open transition over  $J'$
+		and  $\mathcal{S}$.
+
+	\end{itemize}
+
+We take in this article a semantics and logical understanding of these
+automata. Open automata are closed by a simple form of refinement that
+allows us to refine the predicate, or substitute any free variable by
+an expression. More formally, let $\Pred$ be any predicate and $\psi$ any effect such that $V\cap \dom(\psi)=\emptyset$. Then we have the following
+implication:
+
+	 \begin{mathpar}
+    \openrule
+         {
+           \set{\beta}, \Pred\,',\phi}
+          {t \OTarrow {\alpha} t'}\in\mathcal{T}
+\implies
+    \openrule
+         {
+           \set{\psi(\beta)}, \psi(\Pred)\land\Pred,\phi\circ\psi}
+         {\raisemath{-2pt}{t \OTarrow {\psi(\alpha)} {t'}}{}}
+ \in\mathcal{T}
+\end{mathpar}
+\end{definition}
+
+An operational interpretation of the open automaton and transition is naturally to build an automaton where states are couple (state identifier, variable valuation).
+A variable valuation $\sigma$ maps variables to values. Similarly to effect, we use the notation $\sigma(e)$ to mean the evaluation of $e$ where variables have been instantiated by $\sigma$.
+Consider  $A =
+	\mylangle J,\mathcal{S},s_0,V,\mathcal{T}\myrangle$. Suppose $\dom(\sigma)=V$
+We can build it for an open automaton without hole as follows (we obtain a concrete automaton $\mathcal{T'}$ from $\mathcal{T}$):
+
+\begin{mathpar}
+\inferrule
+{\openrule
+         {
+           \emptyset, \Pred,\phi}
+          {s \OTarrow {\alpha} s'}\in\mathcal{T}
+\\
+\dom(\psi)=\fv(\alpha)\setminus V
+\\
+(\psi\uplus\sigma)(\Pred)
+}
+{(s,\sigma)\xrightarrow{(\psi\uplus\sigma)(\alpha)}(s',\sigma\circ\phi\circ\psi)\in\mathcal{T'}}
+\end{mathpar}
+
+\TODO{We could add a set of automata in the state to take into account automata filling holes}
+
+Composition: consider two rules obtained as above:
+\begin{mathpar}
+\inferrule
+{(s,\sigma)\xrightarrow{(\psi\uplus\sigma)(\alpha)}(s',\sigma\circ\phi\circ\psi)\in\mathcal{T'}
+\\
+(s',\sigma\circ\phi\circ\psi)\xrightarrow{(\psi'\uplus\sigma')(\alpha')}(s'',\sigma\circ\phi\circ\psi\circ\phi'\circ\psi')\in\mathcal{T'}
+}
+{(s,\sigma)\xrightarrow{(\psi\uplus\sigma)(\alpha)~.~(\psi'\uplus\sigma\circ\phi\circ\psi)(\alpha')}(s'',\sigma\circ\phi\circ\psi\circ\phi'\circ\psi')\in\mathcal{T'}}
+\end{mathpar}
+
+Because of the semantic interpretation of open automata, the set of open transition of an open automaton is infinite (for example because every free variable can be renamed).
+However an open automaton is characterized by a  subset of these open transition which is sufficient to generate, by substitution the other ones.
+In the following, we will abusively write that we define an ``open automaton'' when we provide only the set of open transitions that is sufficient to generate a proper open automaton by saturating each open transition by all possible substitutions and refinements.
+
+Another consequence of the semantics and logical interpretation of the
+formulas is that we make no distinction between the equality and the
+equivalence on boolean formulas, i.e. equivalence of two predicates
+$\Pred$ and $\Pred\,'$ can be denoted $\Pred=\Pred\,'$.
+
+Though the definition is simple, the fact that transitions are complex structures relating events must not be underestimated in order to understand the rest of the article.
+The first element of theory for open automata, i.e.
+the definition of a strong bisimulation, is given below.
+
+\subsection{Bisimulation for open Automata}
+\label{section:bisimulation}
+
+The equivalence we need is a strong bisimulation between
+open automata having exactly the same holes (same indexes and same sorts), but using a
+flexible matching 
+between open transitions, this will allow us to compare pNets
+with different architectures.
+
+We define now a bisimulation relation adapted to open automata and their parametric nature.
+The relation relates states of the open automaton and states equivalence between the open transitions between the states.
+Its key characteristics are 1) the introduction of predicates in the bisimulation relation: as states may contain variables, relation between states may depend on the value of the variables; 2) the bisimulation property relates elements of the open transitions and take into account predicates over variables, actions of the holes, and state modifications.
+ We name it FH-bisimulation,
+ as a short cut for the ``Formal Hypotheses'' over the holes behaviour manipulated in the
+ transitions, but also as a reference to the work of De Simone~\cite{deSimone85},
+ that pioneered this idea.
+
+A relation over the states of two open automata  $\mylangle J,\mathcal{S}_1, s_0,V_1,
+   \mathcal{T}_1 \myrangle$ and $\mylangle !J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2 \myrangle$ has the form $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$, it relates states of $\mathcal{S}_1$ and 
+$\mathcal{S}_2$ constrained by a predicate.
+More precisely, for any pair $(s,t)\in \mathcal{S}_1\times \mathcal{S}_2$, there is a 
+   single
+      $(s,t|\Pred_{s,t})\in\mathcal{R}$  stating that $s$ and $t$ are related 
+      if $\Pred_{s,t}$       is 
+      True, i.e. the states are related when the variables in $V_1$ and $V_2$ verify the 
+      predicate $\Pred_{s,t}$. By nature, this is well-defined if the variables of the two open automata are disjoint, i.e.  $V_1\cap V_2=\emptyset$.
+ FH-bisimulation is defined formally: 
+ \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim} ~\\
+\noindent
+\begin{minipage}{0.67\linewidth} 	Suppose 
+   $A_1 = \mylangle J,\mathcal{S}_1, s_0,V_1,
+   \mathcal{T}_1 \myrangle$ and $A_2 = \mylangle J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2 \myrangle$
+   are open automata with identical holes of the same sort, with disjoint sets of variables.
+
+ Then 
+$\mathcal{R}$ is an FH-bisimulation if and only if for any  states
+$s\in\mathcal{S}_1$ and $t\in\mathcal{S}_2$, $(s,t|\Pred_{s,t})\in\mathcal{R}$, we 
+have
+the following:
+\end{minipage}
+\hspace{2mm}
+\begin{minipage}{0.30\linewidth}
+%	\includegraphics[width=\linewidth]{XFIG/Bisim.pdf}
+\end{minipage}
+
+ \begin{itemize}
+ \item  For any open transition $OT$ in $\mathcal{T}_1$:
+ \begin{mathpar}
+     \openrule
+         {
+           \beta_j^{j\in J'},\Pred_{OT},\Post_{OT}}
+         {s \OTarrow {\alpha} s'}
+
+\end{mathpar}
+ there exist   open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
+ \begin{mathpar}
+%    \left( fresh \ \set{\alpha_i}, \set{b_j}, v_x.\ \
+    \openrule
+         {
+           \beta_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {t \OTarrow {\alpha_x} t_x}
+%         \right)
+\end{mathpar}
+ such that  $\forall x.\, J'=J_{x}$ and there exists $\Pred_{s',t_x}$ such that $(s',t_x|\Pred_{s',t_x})\in 
+ \mathcal{R}$
+ and  \\
+ $\Pred_{s,t} \land \Pred_{OT}\implies$\\
+%\hspace{1cm}
+ $\displaystyle{\bigvee_{x\in X}
+   \left( \forall j. \beta_j=\beta_{jx}  \land \Pred_{OT_x}
+     \land \alpha\!=\!\alpha_x \land  
+     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}$
+
+ \item  and symmetrically any open transition from $t$ in $\mathcal{T}_2$ can be 
+      covered by a set of transitions from $s$ in $\mathcal{T}_1$.
+ \end{itemize}
+
+ \end{definition}
+Classically, $\Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}$
+applies in parallel the  
+substitutions $\Post_{OT}$ and $\Post_{OT_x}$ (parallelism is crucial
+inside each $\Post$ set but not between  $\Post_{OT}$ and
+$\Post_{OT_x}$ that are independent), applying the assignments of the involved rules.
+We can prove that such a bisimulation is an equivalence relation.
+
+\begin{theorem}[FH-Bisimulation is an equivalence]\label{thm-equiv} Suppose $\mathcal{R}$ 
+is an FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
+reflexive, symmetric and transitive.
+\end{theorem}
+
+The proof of this theorem can be found in Annex~\ref{thm-equiv-proof}. The
+only non-trivial part of the proof is the proof of transitivity. It
+relies on the following elements. First,  the transitive composition
+of two relations with predicate is defined; this is not exactly
+standard as it requires to define the right predicate for the
+transitive composition and producing a single predicate to relate any
+two states. Then the fact that one open transition is simulated by a
+family of open transitions leads to a doubly indexed family of
+simulating open transition; this needs particular care, also because
+of the use of renaming (\Post) when proving that the predicates
+satisfy the definition (property on $\Pred_{s,t} \land \Pred_{OT}$ in
+the definition).
+
+\medskip
+
+\subsubsection*{Finite versus infinite open automata, and decidability:} 
+As mentioned in Definition \pageref{def:open-automaton}, we adopt here a semantic view on open automata. More precisely, in \cite{hou:hal-02406098}, we formerly define
+\emph{semantic open automata} (infinite as in Definition \ref{def:open-automaton}),
+and \emph{structural open automata} (finite) that can be generated as
+the semantics of pNets (see Definition \ref{def:operationalSemantics}), and used in the implementation. Then we define
+an alternative version of our bisimulation, called
+structural-FH-Bisimulation, based on structural open automata, and
+prove that the \emph{semantic} and \emph{structural} FH-Bisimulations coincide.
+In the sequel, all mentions of finite automata, and algorithms for
+bisimulations, implicitly refer to their \emph{structural} versions.
+
+If we assume that everything is finite (states and transitions in the
+open automata, and the predicates in $\mathcal{R}$), then it is easy to
+prove that it is decidable whether a relation is a 
+FH-bisimulation, provided the logic of the predicates is
+decidable (proof can be found in \cite{henrio:Forte2016}). Formally:
+
+\begin{theorem}[Decidability of FH-bisimulation]
+Let $A_1$ and $A_2$ be finite open automata
+and $\mathcal{R}$ a relation over their states $\mathcal{S}_1$ and
+$\mathcal{S}_2$ constrained by a finite set of predicates. Assume that
+the predicates inclusion is decidable over  
+the action algebra $\AlgA$. Then it is decidable whether the relation 
+$\mathcal{R}$ is a FH-bisimulation.
+
+\end{theorem}
+
+\section{Weak bisimulation}\label{sec:weak}
+
+Weak symbolic bisimulation was introduced to relate transition systems
+that have indistinguishable behaviour, with respect to some definition
+of \emph{internal actions} that are considered local to some
+subsystem, and consequently cannot be observed, nor used for
+synchronisation with their context.
+The notion of non-observable actions varies in different contexts,
+e.g. $tau$ in CCS, and $i$ in Lotos, we could define classically a set of
+\emph{internal/non-observable actions} depending on a specific action
+algebra. In this paper, to simplify the notations, we will simply use $\tau$ as the single non-observable action; the generalisation of our results to a set of non-observable actions is trivial. 
+Naturally, a non-observable action cannot be synchronised with
+actions of other systems in its environment. 
+We show here that under such assumption of non-observability of $\tau$ actions, see Definition~\ref{def:Non-ObsTau}, we can define a weak bisimulation relation that is compositional, in the sense of open pNet composition.
+In this section we will first define a notion of weak open transition similar to open transition.
+In fact a weak open transition is made of several open transitions labelled as non-observable transitions, plus potentially one observable open transition.
+This allows us to define weak open automata, and a weak bisimulation relation based on these weak open automata.
+Finally, we apply this weak bisimulation to open pNets, obtain a weak bisimilarity relationship for open pNets, and prove that this relation has compositional properties.
+
+%% \TODO{we should understand if it make sense to distinguish invisible
+%%   from synchronised actions: in the Forte paper we wrote ``using  as 
+%% \emph{invisible actions} a subset of the
+%% \emph{synchronised actions} defined in Section~\ref{section:pnets}''}.
+
+%% Proving bisimulation properties on our hierarchical broadcast example
+%% would take too much space for this paper. Moreover, interesting
+%% properties of the HB example would rather be adequate for weak
+%% bisimulation, and its large state-space would require some
+%% tool-assistance, both for the generation of the open-automata and for
+%% their comparison.
+
+\subsection{Preliminary definitions and notations}
+
+We first specify in terms of open transition, what it means for an action to be non-observable.
+Namely, we constraint ourselves to system where the emission of a $\tau$ action by a sub-pNet cannot be observed by the surrounding pNets.
+In other words, a pNet cannot change its state, or emit a specific observable action when one of its holes emits a $\tau$ action.
+
+More precisely, we state that $\tau$ is not observable if the automaton always allows any $\tau$ transition from holes, and additionally the global transition resulting from a $\tau$ action of a hole is a $\tau$ transition not changing the pNet's state.
+We define $\Id(V)$ as the identity function on the set of variables $V$.
+\begin{definition}[Non-observability of $\tau$ actions for open automata]\label{def:Non-ObsTau}
+An open automaton $A = \mylangle J,\mathcal{S},s_0,V,\mathcal{T}\myrangle$ \emph{cannot observe $\tau$ actions} if and only if for all $j$ in $J$ and $s$ in $\mathcal{S}$ we have:
+\begin{enumerate}
+\item
+\[ \openrule
+         {
+           (j\mapsto\tau),\True,\Id(V)}
+         {s \OTarrow {\tau} s}
+         \in \mathcal{T}
+\]
+and 
+\item for all $\beta_j$, $J$,  $\alpha$,  $s$, $s'$, $\Pred$, $\Post$  such that
+\[ \openrule
+         {
+           \beta_j^{j\in J},\Pred,\Post}
+         {s \OTarrow {\alpha} s'}
+         \in \mathcal{T} \] If there exists $j$ such that $\beta_j=\tau$ then we have: \[ \alpha=\tau\land s=s'\land \Pred=\True\land\Post=\Id(V) \land J=\{j\}
+\]
+\end{enumerate}
+\end{definition}
+The first statement of the definition states that the open automaton must allow a hole to do a silent action at any time, and must not observe it, i.e.
+cannot change its internal state because a hole did a $\tau$ transition.
+The second statement ensures that there cannot be in the open automaton other transitions that would be able to observe a $\tau$ action from a hole.
+The condition $J=\{j\}$ is a bit restrictive, it could safely be replaced by $\forall j\in J.\, \beta_j=\tau$, allowing the other holes to perform $\tau$ transitions too (because these $\tau$ actions cannot be observed).
+
+By definition, one weak open transition contains  several open transitions, where  each open transition can require an observable action from a given hole, the same hole might have to emit several observable actions for a single weak open transition to occur.
+Consequently, for a weak open transition to trigger, a sequence of actions from a given hole may be required.
+
+Thus, we let $\gamma$ range over sequences of action terms and use $\dotcup$ as the concatenation operator that appends sequences of action terms: given two sequences of action terms  $\gamma\dotcup\gamma '$ concatenates the two sequences.
+The operation is lifted to indexed sets of sequences:   at each index $i$, $\set {\gamma_1}\dotcup \set {\gamma_2}$ concatenates the sequences of actions at index $i$ of $\set{\gamma_1}$ and the one at index $i$ of $\set {\gamma_2}$\footnote{One of the two sequences is empty when $i\not \in \dom(\set{\gamma_1})$ or $i\not \in \dom(\set{\gamma_2})$ .}.
+$[a]$ denotes a sequence with a single element.
+
+As required actions are now sequences of observable actions, we need an operator to build them from set of actions that occur in open transitions, i.e.
+an operator that takes a set of actions performed by one hole and produces a sequence of observable actions.
+
+Thus we define $\vis{\set\beta}$ as the mapping $\set\beta$  with only observable actions of the holes in $I$, but where each element is either empty or a list of length 1:
+ \[\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}\text{ where }I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}\]
+
+As an example the $\vis{\set\beta}$ built from the transition $OT_1$ in Example~\ref{OT:SimpleProt}, page \pageref{OT:SimpleProt} is $\texttt{P}\mapsto [\texttt{p-send(m)}]$.
+Remark that in our simple example no $\tau$ transition involves any visible action from a hole, so we have no $\beta$ sequences of length longer than 1 in the weak automaton.
+%\TODO{en fait c'est faux ! les boucles SS\_1, SS\_2, WS\_1, WS\_2 sont aussi valides avec p\_a ou q\_b = tau, donc on peut avoir des sequences de longueur arbitraire d'actions de P et de Q}
+
+\subsection{Weak open transition definition}
+
+Because of the non-observability property (Definition~\ref{def:Non-ObsTau}), it is possible to add any number of $\tau$ transitions of the holes before or after any open transition freely.
+This property justifies the fact that we can abstract away $\tau$ transitions from holes in the definition of a weak open transition.
+
+%
+%Classically, we start by defining a derived transition relation based
+%on sequences of invisible actions.
+
+\def\InvAct{\mathcal{Inv}}
+%
+%\RAB{We let $\gamma$ range over words (of action terms) and use $\dotcup$ as the union that appends words.}
+
+\begin{definition}[Weak open transition (WOT)]\label{def:weakOT}
+A weak open transition over a
+	set $J$ of holes with sorts $\Sort_j^{j\in J}$ and a set of states $\mathcal{S}$ is 
+	a structure of the form:	
+\begin{mathpar}
+ \openrule
+         {
+           \gamma_j^{j\in J'},\Pred,\Post}
+         {s \OTWeakarrow {\alpha} s'}
+ \end{mathpar}
+	Where $J'\subseteq J$, $s, s'\in\mathcal{S}$ and $\gamma_j$
+        is a list of transitions of the hole $j$, with each element of the list in $\Sort_j$. $\alpha$ is an action 
+        label denoting the resulting action
+        of this open transition. \Pred\ and \Post\ are defined similarly to Definition~\ref{def:OT}. We use $\WT$ to range over sets of weak open transitions.
+
+A weak open automaton $\mylangle J,\mathcal{S},s_0,V,\WT\myrangle$ is similar to an open automaton  except that $\WT$ is a set of weak open transitions over $J$ and $\mathcal{S}$.
+\end{definition}
+
+A weak open transition labelled $\alpha$ can be seen as a sequence of open transitions that are all labelled $\tau$ except one that is labelled $\alpha$; however conditions on predicates, effects, and states must be verified for this sequence to be fired.
+
+We are now able to build a weak open automaton from an open automaton.
+This is done in a way that resembles the process of $\tau$ saturation: we add  $\tau$ open transitions before or after another (observable or not) open transition.
+\begin{definition}[Building a weak open automaton]\label{def:buildweakOT}
+  Let $A = \mylangle J,\mathcal{S},s_0,V,\mathcal{T}\myrangle$ be an open automaton. 
+The weak open automaton \emph{derived} from $A$ is an open automaton  $\mylangle J,\mathcal{S},s_0,V,\WT\myrangle$ where $\WT$ is derived from $\mathcal{T}$ by saturation, applying the following rules:
+%\noindent{\bf Invisible $\tau$ transitions:}
+\begin{mathpar}
+ \openrule
+         {
+           \emptyset,\symb{True},\Id(V)}
+         {s \OTWeakarrow {\tau} s} \in \WT  \qquad \WTUn
+ \end{mathpar}
+and
+\begin{mathpar}
+\inferrule{
+ \openrule
+         {
+           \set{\beta},\Pred,\Post}
+         {s \OTarrow {\alpha} s'} \in \mathcal{T}
+} 
+{ \openrule
+         {
+           \vis{\set{\beta}}\!,\Pred,\Post
+				 } {s \OTWeakarrow {\alpha} s'} \in \WT
+}\qquad \WTDeux
+%\inferrule{
+% \openrule
+%         {
+%           \set{\beta},\Pred,\Post}
+%         {s \OTarrow {\tau} s'} \in \mathcal{T}
+%\\
+% \openrule
+%         {
+%           \set{\gamma},\Pred\,',({x_k\gets e_k})^{k\in K}   }
+%         {s' \OTWeakarrow {\tau} s''} \in \WT
+%}
+%{ \openrule
+%         {
+%           \vis{\set{\beta}}\dotcup\set{\gamma},\Pred\land\Pred\,'\subst{\Post\,},
+%				({x_k\gets (e_k\subst{\Post\,})})^{k\in K} } 
+%         {s \OTWeakarrow {\tau} s''} \in \WT
+%}
+ \end{mathpar}
+ and
+%\noindent{\bf Other transitions:}
+\begin{mathpar}
+\inferrule {\openrule
+         {
+           \set{\gamma_1},\Pred_1,\Post_1   }
+         {s \OTWeakarrow {\tau} s_1} \in \WT
+\qquad
+\openrule
+         {
+           \set{\gamma_2},\Pred_2,\Post_2  }
+         {s_1 \OTWeakarrow {\alpha} s_2} \in \WT
+\qquad
+\openrule
+         {
+           \set{\gamma_3},\Pred_3,\Post_3  }
+         {s_2 \OTWeakarrow {\tau} s'} \in\WT
+\\
+\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land \Pred_3\subst{\Post_2\shortotimes\Post_1}
+\\
+\set{\gamma}=\set{\gamma_1}\dotcup \set{\gamma_2}\subst{\Post_1}\dotcup\set{\gamma_3}\subst{\Post_2\shortotimes \Post_1}\\
+\alpha'=\alpha\subst{\Post_1}
+}
+{
+\openrule
+         {\set{\gamma}
+           ,
+		\Pred,
+				\Post_3\shortotimes\Post_2\shortotimes\Post_1} 
+         {s \OTWeakarrow {\alpha'} s'} \in\WT
+} \WTTrois
+\end{mathpar}
+
+\end{definition}
+Rule $\WTUn$ states that it is always possible to do a non-observable transition, where the state is unchanged and the holes perform no action.
+Rule~$\WTDeux$ states that each open transition can be considered as a weak open transition.
+The last rule is the most interesting:  Rule~$\WTTrois$ allows any number of $\tau$ transitions before or after any weak open transition.
+This rules carefully composes predicates, effects, and actions of the holes, indeed in the rule, predicate $\Pred_2$ manipulates variables of $s_1$ that result from the first weak open transition.
+Their values thus depend on the initial state but also on the effect (as a substitution $\Post_1$) of the first weak open transition.
+In the same manner, $\Pred_3$ must be applied the joint substitution $\Post_2\shortotimes\Post_1$.
+Similarly, effects on variables must be applied to obtain the global effect of the composed weak open transition, it must also be applied to observable actions of the holes, and to the global action of the weak open transition.
+
+\subsection{Composition properties: composition of weak open transitions}
+We now have two different semantics for open pNets: a strong semantics, defined  as an open automaton, and as a weak semantics, defined as a weak open automaton.
+Like the open automaton, the weak open automaton features valuable composition properties.
+We can exhibit  a composition property and a decomposition property that relate open pNet composition with their semantics, defined as weak open automata.
+These are however technically more complex than the ones for open automata because each hole performs a set of actions, and thus a composed transition is the composition of one transition of the top-level pNet and a sequence of transitions of the sub-pNet that fills its hole.
+They can be found as Lemmas~\ref{lem-decomposeWOT}, Lemma~\ref{lem-Weakcompose1}, and Lemma~\ref{lem-Weakcompose} in Appendix~\ref{sec:app-composition}.
+
+\subsection{Weak FH-bisimulation}
+For defining a bisimulation relation between weak open automata, two options are possible.
+Either we define a simulation similar to the strong simulation but based on open automata, this would look like the FH-simulation but would need to be adapted to weak open transitions.
+Or we define directly and classically a weak FH-simulation as a relation between two open automata, relating the open transition of the first one with the transition of the weak open automaton derived from the second one.
+
+The definition below specifies how a set of weak open transitions can simulate an open transition, and under which condition; this is used to relate, by weak FH-bisimulation, two open automata by reasoning on the weak open automata that can be derived from the strong ones.
+This is defined formally as follows.
+
+\begin{definition}[Weak FH-bisimulation]\label{def-Weak-bisim} ~\\
+\noindent
+Let $A_1 = \mylangle J,\mathcal{S}_1, s_0,V_1,
+    \mathcal{T}_1\myrangle$ and $A_2 = \mylangle J,\mathcal{S}_2,t_0, V_2, \mathcal{T}_2\myrangle$ be open automata with disjoint sets of variables.
+Let $\mylangle J,\mathcal{S}_1, s_0,V_1,
+    \WT_1\myrangle$ and $\mylangle J,\mathcal{S}_2,t_0, V_2, \WT_2\myrangle$ be the
+weak open automata derived from $A_1$ and $A_2$ respectively.
+Let $\mathcal{R}$ a relation over
+$\mathcal{S}_1$ and $\mathcal{S}_2$, as in Definition~\ref{def-FH-bisim}.
+
+Then 
+   $\mathcal{R}$ is a weak FH-bisimulation iff for any  states
+$s\in\mathcal{S}_1$ and
+$t\in\mathcal{S}_2$ such that $(s,t|\Pred)\in\mathcal{R}$, we 
+   have the following:
+
+ \begin{itemize}
+ \item  For any open transition $OT$ in $\mathcal{T}_1$:
+ \begin{mathpar}
+     \openrule
+         {
+           \beta_j^{j\in J'},\Pred_{OT},\Post_{OT}}
+         {s \OTarrow {\alpha} s'}
+
+\end{mathpar}
+ there exist weak open transitions $\symb{WOT}_x^{\;x\in X} \subseteq \WT_2$:
+ \begin{mathpar}
+    \openrule
+         {
+           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {t \OTWeakarrow {\alpha_x} t_x}
+\end{mathpar}
+ such that  $\forall x.\, \{j\in J'|\beta_j\neq\tau\}=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
+ and  \\
+ $\Pred \land \Pred_{OT}\\
+\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
+   \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
+     \!\land\! \alpha\!=\!\alpha_x\! \land\!  
+     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}$
+
+ \item  and symmetrically any open transition from $t$ in $\mathcal{T}_2$ can be 
+      covered by a set of weak transitions from $s$ in $\WT_1$.
+ \end{itemize}
+
+Two pNets are weak FH-bisimilar if there exists a relation between their associated 
+automata that is a Weak FH-bisimulation and their initial states are in the relation, i.e. 
+the predicate associated to the relation between the initial states is \True.
+ \end{definition}
+
+Compared to strong bisimulation, except the obvious use of weak open transitions to simulate an open transition, the condition on predicate is slightly changed concerning actions of the holes.
+Indeed only the visible actions of the holes must be compared and they form a list of actions, but of length at most one.
+
+Our first important result is that Weak FH-bisimilarity is an equivalence in the same way as strong FH-bisimilarity:
+
+\begin{theorem}[Weak FH-Bisimulation is an equivalence]\label{thm-weak-equiv} Suppose $\mathcal{R}$ 
+is a weak FH-bisimulation. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
+reflexive, symmetric and transitive.
+\end{theorem}
+The proof  is detailed in Appendix \ref{app-WFH-equiv}, it follows a similar pattern as the proof that strong FH-bisimulation is an equivalence, but technical details are different, and in practice we rely on a variant of the definition of weak FH-bisimilarity; this equivalent version simulates a \emph{weak} open transition with a set of weak open transition.
+The careful use of the best definition of weak FH-bisimilarity makes the proof similar to the strong FH-bisimulation case.
+
+\subsubsection*{Proving bisimulation in practice}
+
+In practice, we are dealing with finite representations of the (infinite) open automata.
+In \cite{hou:hal-02406098}, we defined a slightly modified definition of the ``coverage'' proof obligation, in the case of strong FH-Bisimulation.
+This modification is required to manage in a finite way all possible instantiations of an OT.
+In the case of weak FH-Bisimulation, the proof obligation from Definition \ref{def-Weak-bisim} becomes:
+      \begin{multline*}
+\forall fv_{OT}.\, \Big\{ \Pred \land \Pred_{OT} \implies\\
+ \bigvee_{x\in X}\!
+  \left[\exists fv_{OT_x}.
+    \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
+     \!\land\! \alpha\!=\!\alpha_x\! \land\!  
+     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)\right]\Big\}
+\end{multline*}
+
+In which $fv_{OT}$ denotes the set of free variables of all expressions in $OT$.
+
+\bibliographystyle{lncs/splncs}
+
+% \bibliography{oasis,biblio}
+\bibliography{biblio}
+
+\newpage
+\appendix
+
+\section{Parameterised Networks (pNets)}
 \label{section:pnets}
@@
 
-\subsection{Running Example}
-To illustrate this work, we use a simple communication protocol, that provides safe transport of data between two processes, over unsafe media.
-
-Figure \ref{SimpleProt:Spec} (left) shows the example principle, which corresponds to the hierarchical structure of a pNet: two unspecified
-processes $P$ and $Q$ (holes) communicate messages, with a data value
-argument, through the two protocol entities.
-Process $P$ sends an $\texttt{p-send(m)}$ message to the $\symb{Sender}$; this communication is denoted as $\texttt{\nounderline{in(m)}}$% , where underline actions represent internal actions that cannot be further synchronised with the environment, similarly to the $\tau$ of CCS.
-In our formalisation we will also denote these actions $\tau$ for simplicity of notations but the examples are easier to read when invisible actions have significant names}
-.
-At the other end, process $Q$ receives the message from the $\symb{Receiver}$.
-The holes $P$ and $Q$ can also have other interactions with their environment, represented here by actions $\texttt{p-a}$ and $\texttt{q-b}$.
-The underlying network is modelled by a medium entity transporting messages from the sender to the receiver, and that is able to detect transport errors and signal them to the sender.
-The return $\symb{ack}$ message from $\symb{Receiver}$ to $\symb{Sender}$ is supposed to be safe.
-The final transmission of the message to the recipient (the hole $Q$) includes the value of the ``error counter'' $ec$.
-
-Figure \ref{SimpleProt:Spec} (right) shows a graphical view of the pNet that specifies the system:
-the full system should be equivalent (e.g.  weakly bisimilar)
-to the two processes connected simply through a perfect medium.  
-The pNet has a tree-like structure.
-The root node of the tree {\it SimpleSystemSpec} is the top level of the pNet structure.
-It acts as the parallel operator.
-It consists of three nodes: two holes $P$ and $Q$ and one sub-pNet, denoted {\it PrefectBuffer}.
-Nodes of the tree are synchronized using four synchronization vectors, that  express the possible synchronizations between the parameterised actions of a subset of the nodes.
-For instance, in the vector "$< \texttt{p-send(m)},\texttt{in(m)},\_> \rightarrow \texttt{\nounderline{in(m)}}$" only $P$ and {\it PrefectBuffer} nodes are involved in the synchronization.
-The synchronization between these processes occurs when  process $P$  performs $\texttt{p-send(m)}$  action sending a message, and  the {\it PrefectBuffer} accepts the message through an $\texttt{in(m)}$ action  at the same time; the result that will be returned at upper level is the action  $\texttt{\nounderline{in(m)}}$.
-
-Figure \ref{SimpleProt:Impl} shows the pNet model of the protocol implementation.
-When the $\symb{Medium}$ detects an error (modelled by a local $\tau$ action), it sends back a $\texttt{m-error}$ message to the $\symb{Sender}$.
-The $\symb{Sender}$ increments its local error counter $ec$, and resends the message (including $ec$) to the $\symb{Medium}$, that will, eventually, transmit $m,ec$ to the $\symb{Receiver}$.
-%Strictly speaking, as variables are local to each  state, we have two distinct $ec$ variables in the \textit{Sender} pLTS, one in state \texttt{s1}, another one in state \texttt{s2}, the value of the variable is updated along the transitions entering each of the two states.
-
-\begin{figure}[t]
-   \includegraphics[width=.37\textwidth]{XFIG/SimpleProt-Schema}
-   \includegraphics[width=.62\textwidth]{XFIG/SimpleProt2-Spec}
-   \caption{pNet structure of the example and specification expressed as a pNet}
-   \label{SimpleProt:Spec}
-
-\end{figure}
-
-\begin{figure}[t]
-  \centerline{\includegraphics[width=.95\textwidth]{XFIG/SimpleProt2-pNet-tau}}
-  \caption{Composed pNet with the Simple Protocol Implementation}  \label{SimpleProt:Impl}
-\end{figure}
-
-\section{A model of process composition}\label{sec:OT}
-
-The semantics of open pNets will be defined  as an open automaton. An open
-automaton is an automaton where each transition composes transitions of several LTSs with
-action of some holes, the transition occurs if some predicates hold, and can involve a 
-set of state modifications.
-This section defines open automata and a bisimulation theory for them.
-This section can be viewed as an improved version of the formalism described in \cite{henrio:Forte2016}, extending the automata with a notion of global variable, which makes the state of the automaton more explicit.
-We also adopt a semantics and logical interpretation of the automata that intuitively can be stated as follows: ``if a transition belongs to an open automaton, any refinement of this transition also belongs to the automaton''.
-
-\subsection{Open Automata}
- Open automata (OA) are not composition structures but they are made of transitions that are dependent of the actions of the holes, and they can reason on a set of variables (potentially with only symbolic values).
-%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
-%different 
-%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
-\begin{definition}[Open transitions]\label{def:OT}
-	\label{def:OpenTransitions}
-	An \emph{open transition} (OT) over a
-	set $J$ of holes with sorts $\Sort_j^{j\in J}$, a set $V$ of variables, and a set of states $\mathcal{S}$ is 
-	a structure of the form:	
-	\begin{mathpar}
-	\openrule
-	{	\beta_j^{j\in J'}, \Pred, \Post}
-	{s \OTarrow {\alpha}s'}
-	\end{mathpar}
-	Where $J'\subseteq J$, $s, s'\in\mathcal{S}$ and $\beta_j$
-        is a transition of the hole $j$, with $\beta_j\in\Sort_j$. $\alpha$ is an action 
-        label denoting the resulting action of this open transition.
-%        We call \emph{source variables} of an OT the union of all variables
-%        in the different terms
-%        $\beta_j$ and $\alpha$, and the state variables of $s$.
-        \Pred\ is a predicate over the  variables in $V$ and all variables
-        in the different terms
-       $\beta_j$ and $\alpha$. \Post\ is a set of 
-	assignments that are effective after the open transition, they are
-        represented as a substitution of the form $({x_k\gets e_k})^{k\in K}$ 
-	where $\forall k.\, x_k\in V$, and $e_k$ are expressions
-        over the variables $V$ and all variables
-        in the different terms
-       $\beta_j$ and $\alpha$. The assignments are always applied simultaneously because the variables in $V$ can be in both sides. Open transitions are identified
-        modulo logical equivalence on their predicate. 
-\end{definition}
-
-It is important to understand the difference between the red dotted rule and a normal 
-inference rule. They correspond to two different logical levels.
-On one side, classical (black) inference rules  use  an expressive logic and are paper rules.
- On the other side, open transition rules (with dotted lines) are logical implications, but using a simple logic (this logic includes the boolean expressions $\AlgB$, boolean operators, and term equality).
-   open transitions could typically be handled in a 
- mechanised way.
-
-An open automaton is  an automaton where each transition is an open transition.
-\begin{definition}[Open automaton]
-	\label{def:open-automaton}
-	An \emph{open automaton} is a structure\\ $A =
-	\mylangle J,\mathcal{S},s_0,V,\mathcal{T}\myrangle$ where:
-	\begin{itemize}
-		\item[$\bullet$]   $J$ is a  set of indices.
-		\item[$\bullet$]   $\mathcal{S}$ is a set of states and $s_0$ an initial state
-		  among $\mathcal{S}$.
-%       \item[$\bullet$] for each state $s$, $vars(s)=\{v_s\}$ is a set of state variables, 
- \item[$\bullet$] $V$ is a set of variables of the automaton
-		and each $v\in V$ may have an initial value $init(v)$.
-		\item[$\bullet$] $\mathcal{T}$ is a set of open transitions and for each
-		$t\in \mathcal{T}$ there exist  $J'$ with  $J'
-		\subseteq J$, such that $t$ is an open transition over  $J'$
-		and  $\mathcal{S}$.
-
-	\end{itemize}
-
-We take in this article a semantics and logical understanding of these
-automata. Open automata are closed by a simple form of refinement that
-allows us to refine the predicate, or substitute any free variable by
-an expression. More formally, let $\Pred$ be any predicate and $\Post$ any substitution such that $V\cap \dom(\Post)=\emptyset$. Then we have the following
-implication:
-
-	 \begin{mathpar}
-    \openrule
-         {
-           \set{\beta}, \Pred\,',\Post\,'}
-          {t \OTarrow {\alpha} t'}\in\mathcal{T}
-\implies
-    \openrule
-         {
-           \set{\beta}\subst{\Post}, \Pred\,'\subst{\Post}\land\Pred,\Post\shortotimes\Post\,'}
-         {\raisemath{-2pt}{t \OTarrow {\alpha\subst{\Post}} {t'}}{}}
- \in\mathcal{T}
-\end{mathpar}
-\end{definition}
-
-%\LUDO{I added this paragraph}
-Because of the semantic interpretation of open automata, the set of open transition of an open automaton is infinite (for example because every free variable can be renamed).
-However an open automaton is characterized by a  subset of these open transition which is sufficient to generate, by substitution the other ones.
-In the following, we will abusively write that we define an ``open automaton'' when we provide only the set of open transitions that is sufficient to generate a proper open automaton by saturating each open transition by all possible substitutions and refinements.
-
-Another consequence of the semantics and logical interpretation of the
-formulas is that we make no distinction between the equality and the
-equivalence on boolean formulas, i.e. equivalence of two predicates
-$\Pred$ and $\Pred\,'$ can be denoted $\Pred=\Pred\,'$.
-
-Though the definition is simple, the fact that transitions are complex structures relating events must not be underestimated in order to understand the rest of the article.
-The first element of theory for open automata, i.e.
-the definition of a strong bisimulation, is given below.
-
-\subsection{Bisimulation for open Automata}
-\label{section:bisimulation}
-
-The equivalence we need is a strong bisimulation between
-open automata having exactly the same holes (same indexes and same sorts), but using a
-flexible matching 
-between open transitions, this will allow us to compare pNets
-with different architectures.
-
-We define now a bisimulation relation adapted to open automata and their parametric nature.
-The relation relates states of the open automaton and states equivalence between the open transitions between the states.
-Its key characteristics are 1) the introduction of predicates in the bisimulation relation: as states may contain variables, relation between states may depend on the value of the variables; 2) the bisimulation property relates elements of the open transitions and take into account predicates over variables, actions of the holes, and state modifications.
- We name it FH-bisimulation,
- as a short cut for the ``Formal Hypotheses'' over the holes behaviour manipulated in the
- transitions, but also as a reference to the work of De Simone~\cite{deSimone85},
- that pioneered this idea.
-
-A relation over the states of two open automata  $\mylangle J,\mathcal{S}_1, s_0,V_1,
-   \mathcal{T}_1 \myrangle$ and $\mylangle !J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2 \myrangle$ has the form $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$, it relates states of $\mathcal{S}_1$ and 
-$\mathcal{S}_2$ constrained by a predicate.
-More precisely, for any pair $(s,t)\in \mathcal{S}_1\times \mathcal{S}_2$, there is a 
-   single
-      $(s,t|\Pred_{s,t})\in\mathcal{R}$  stating that $s$ and $t$ are related 
-      if $\Pred_{s,t}$       is 
-      True, i.e. the states are related when the variables in $V_1$ and $V_2$ verify the 
-      predicate $\Pred_{s,t}$. By nature, this is well-defined if the variables of the two open automata are disjoint, i.e.  $V_1\cap V_2=\emptyset$.
- FH-bisimulation is defined formally: 
- \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim} ~\\
-\noindent
-\begin{minipage}{0.67\linewidth} 	Suppose 
-   $A_1 = \mylangle J,\mathcal{S}_1, s_0,V_1,
-   \mathcal{T}_1 \myrangle$ and $A_2 = \mylangle J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2 \myrangle$
-   are open automata with identical holes of the same sort, with disjoint sets of variables.
-
- Then 
-$\mathcal{R}$ is an FH-bisimulation if and only if for any  states
-$s\in\mathcal{S}_1$ and $t\in\mathcal{S}_2$, $(s,t|\Pred_{s,t})\in\mathcal{R}$, we 
-have
-the following:
-\end{minipage}
-\hspace{2mm}
-\begin{minipage}{0.30\linewidth}
-	\includegraphics[width=\linewidth]{XFIG/Bisim}
-\end{minipage}
-
- \begin{itemize}
- \item  For any open transition $OT$ in $\mathcal{T}_1$:
- \begin{mathpar}
-     \openrule
-         {
-           \beta_j^{j\in J'},\Pred_{OT},\Post_{OT}}
-         {s \OTarrow {\alpha} s'}
-
-\end{mathpar}
- there exist   open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
- \begin{mathpar}
-%    \left( fresh \ \set{\alpha_i}, \set{b_j}, v_x.\ \
-    \openrule
-         {
-           \beta_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {t \OTarrow {\alpha_x} t_x}
-%         \right)
-\end{mathpar}
- such that  $\forall x.\, J'=J_{x}$ and there exists $\Pred_{s',t_x}$ such that $(s',t_x|\Pred_{s',t_x})\in 
- \mathcal{R}$
- and  \\
- $\Pred_{s,t} \land \Pred_{OT}\implies$\\
-%\hspace{1cm}
- $\displaystyle{\bigvee_{x\in X}
-   \left( \forall j. \beta_j=\beta_{jx}  \land \Pred_{OT_x}
-     \land \alpha\!=\!\alpha_x \land  
-     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}$
-     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
-     %     \right)$.
-%\bigskip
-%
-% $\Pred_{s,t} \land \Pred_{OT}\implies\bigvee_{x\in X} \Pred_x$
-%and\\
-%%\hspace{1cm}
-% $ \forall{x\in X}. \Pred_x \land \Pred_{s,t} \land \Pred_{OT} \Rightarrow
-%   \left( \forall j. \beta_j=\beta_{jx}  \land \Pred_{OT_x}
-%     \land \alpha\!=\!\alpha_x \land  
-%     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)$
-%     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
-%     %     \right)$.
-
-%     \TODO{Eric: j'ai ajoute $\exists$ sur les predicats $\Pred_{s',t_x}$, qui n'etaient pas definis...}
-
- \item  and symmetrically any open transition from $t$ in $\mathcal{T}_2$ can be 
-      covered by a set of transitions from $s$ in $\mathcal{T}_1$.
- \end{itemize}
-
-% \TODO{Eric: il reste des petits bugs genre $s^{2'}_x$ plutot que
-%   $s^{2}_x$}
-
-%Where $\symb{Subst}(\Pred,\Post)$ is the parallel substitution of all
-%assigned variables.
-
-% \TODO{do we want formulas for this?}
- \end{definition}
-Classically, $\Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}$
-applies in parallel the  
-substitutions $\Post_{OT}$ and $\Post_{OT_x}$ (parallelism is crucial
-inside each $\Post$ set but not between  $\Post_{OT}$ and
-$\Post_{OT_x}$ that are independent), applying the assignments of the involved rules.
-We can prove that such a bisimulation is an equivalence relation.
-
-\begin{theorem}[FH-Bisimulation is an equivalence]\label{thm-equiv} Suppose $\mathcal{R}$ 
-is an FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
-reflexive, symmetric and transitive.
-\end{theorem}
-
-The proof of this theorem can be found in Annex~\ref{thm-equiv-proof}. The
-only non-trivial part of the proof is the proof of transitivity. It
-relies on the following elements. First,  the transitive composition
-of two relations with predicate is defined; this is not exactly
-standard as it requires to define the right predicate for the
-transitive composition and producing a single predicate to relate any
-two states. Then the fact that one open transition is simulated by a
-family of open transitions leads to a doubly indexed family of
-simulating open transition; this needs particular care, also because
-of the use of renaming (\Post) when proving that the predicates
-satisfy the definition (property on $\Pred_{s,t} \land \Pred_{OT}$ in
-the definition).
-
-%\TODO{have a look at the end of the sec}
-
-\medskip
-
-\subsubsection*{Finite versus infinite open automata, and decidability:} 
-As mentioned in Definition \pageref{def:open-automaton}, we adopt here a semantic view on open automata. More precisely, in \cite{hou:hal-02406098}, we formerly define
-\emph{semantic open automata} (infinite as in Definition \ref{def:open-automaton}),
-and \emph{structural open automata} (finite) that can be generated as
-the semantics of pNets (see Definition \ref{def:operationalSemantics}), and used in the implementation. Then we define
-an alternative version of our bisimulation, called
-structural-FH-Bisimulation, based on structural open automata, and
-prove that the \emph{semantic} and \emph{structural} FH-Bisimulations coincide.
-In the sequel, all mentions of finite automata, and algorithms for
-bisimulations, implicitly refer to their \emph{structural} versions.
-
-If we assume that everything is finite (states and transitions in the
-open automata, and the predicates in $\mathcal{R}$), then it is easy to
-prove that it is decidable whether a relation is a 
-FH-bisimulation, provided the logic of the predicates is
-decidable (proof can be found in \cite{henrio:Forte2016}). Formally:
-
-\begin{theorem}[Decidability of FH-bisimulation]
-Let $A_1$ and $A_2$ be finite open automata
-and $\mathcal{R}$ a relation over their states $\mathcal{S}_1$ and
-$\mathcal{S}_2$ constrained by a finite set of predicates. Assume that
-the predicates inclusion is decidable over  
-the action algebra $\AlgA$. Then it is decidable whether the relation 
-$\mathcal{R}$ is a FH-bisimulation.
-
-\end{theorem}
-
 \section{Semantics of Open pNets}
@@
 
-%\TODO{Eric: rewrite example with new Protocolkeep only OT1, and adapt comments}
-\begin{example}[An open-transition]
-  \label{OT:SimpleProt}
-At the upper level, the $\symb{SimpleSystem}$ pNet of Figure \ref{SimpleProt:Impl} has 2 holes and $\symb{SimpleProtocol}$ as
-a sub-pNet, itself containing 3 pLTSs. One of its possible open transitions
-(synchronizing the hole $P$
-with the $\symb{Sender}$ within the \emph{SimpleProtocol}) is:
-
- \smallskip\noindent
- \[  OT_1  = \openrule{
-      \{\texttt{P}\mapsto \texttt{p-send(m)}\},  [\texttt{m=m'}],
-        (\texttt{s\_msg}\gets \texttt{m})
+\section{pNet Composition Properties: composition of open transitions}
+The semantics of open pNets allows us to prove two crucial properties relating pNet composition with pNet semantics: open transition of a composed pNet can be decomposed into open transitions of its composing sub-pNets, and conversely, from the open transitions of sub-pNets,  an open transition of the composed pNet can be built.
+
+We start with decomposition: from one open transition of $P[Q]_{j_0}$, we exhibit 
+corresponding behaviours of $P$ and $Q$, and determine the relation between their 
+predicates:
+\begin{lemma}[Open transition decomposition\label{lem-decompose}] Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$}.
+	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose:
+	\[ P[Q]_{j_0}  
+		\models
+		{\openrule
+			{
+				\beta_j^{j\in J}, \Pred,  
+				\Post}
+			{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
+				\ostate{s_i'^{\, i\in L}}}
 		}
-    {\ostate{s_0,m_0,r_0} \OTarrow{\nounderline{\texttt{in(m')}}} \ostate{s_1,m_0,r_0}}
 	\]
-
-    \smallskip
-    The global states here are triples, build as the product of states of the 3 pLTSs (remember the holes have no state). The assignment
-    $Post$ uses the variable $\texttt{m}$ from the action of hole $\texttt{P}$ to set the
-    value of the sender variable named $\texttt{s\_msg}$.
-
- %%  The \emph{SimpleProtocol} pNet of Fig. \ref{SimpleProt:Spec} has 3 controllers and no holes. One of its possible open-transition (the sender sending $(m)$ to the medium) is:
-
- %% \smallskip\noindent
- %% $  OT_2  = \openrule{
- %%   \emptyset; Pred=[send(SV\_m)=send(s_\_m);in(SV\_m)=in(?m)];  \\ Post=\{m_\_m:=?m\}
- %%                      }
- %%    {\ostate{s_1,m_0,r_0} \OTarrow{\nounderline{send(SV\_m)}} \ostate{s_2,m_1,r_0}}
- %%    $
-
- %%    That can be simplified to:
-
- %%    \ERIC{Apres application des substitutions et simplification du predicat:}
-
- %%     $  OT_2  = \openrule{
- %%      \emptyset; Pred=\True;  \\ Post=\{m_\_m:=s_\_m\}
- %%                      }
- %%    {\ostate{s_1,m_0,r_0} \OTarrow{\nounderline{send(s_\_m)}} \ostate{s_2,m_1,r_0}}
- %%    $
-
- %%    \smallskip
- %%    Note that the global states shows how the sender and the
- %%    first medium have evolved during this transition, the sender
- %%    moving from $s_1$ to $s_2$, and the first (forward) medium from
- %%    $m_0$ to $m_1$.
- %%    The predicate $Pred$ involves the state variables $s_\_m$ and
- %%    $s_\_sb$ of the sender, while the assignment $Post$ sets the
- %%    state variables of the medium.
-
-    \smallskip
-
-\end{example}
+		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.
+		 Then there exist $\alpha_Q$, $\Pred\,'$, $\Pred\,''$, 
+		$\Post\,'$, $\Post\,''$ s.t.:\\[-2ex]
+		%\[
+		\begin{mathpar}
+		P\models{\openrule
+			{
+				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
+				\Pred\,',  
+				\Post\,'}
+			{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {\alpha}
+				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
+		}%\]
+	\vspace{-2.2ex}\\\text{and~~}
+		%\[
+		Q\models{\openrule
+			{
+				\beta_j^{j\in J\cap\Holes(Q)}, \Pred\,'',  
+				\Post\,''}
+			{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
+				\ostate{s_i'^{\,i\in L_Q}}}
+		}%\]
+		\end{mathpar}
+		and  $\Pred \iff \Pred\,'
+		\land \Pred\,''\land \alpha_Q=\beta_{j_0}$, $\Post=\Post\,'\uplus 
+		\Post\,''$ where $\Post\,''$ is the restriction of $\Post$ over variables of 
+		$Q$.
+\end{lemma}
+
+Lemma \ref{lem-compose} is combining an open transition of $P$ with
+an open transition of $Q$, and building a corresponding transition of
+$P[Q]_{j_0}$, assembling their predicates.
+
+\begin{lemma}[Open transition composition]\label{lem-compose} 
+	Suppose $j_0\in J$ and:\\[-2ex]
+\begin{mathpar}
+%\[
+P\models{\openrule
+	{
+		\beta_j^{j\in J}, 
+		\Pred,  
+		\Post}
+	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
+		\ostate{s_i'^{\, i\in L}}}
+}%\]
+\text{~~and~~}
+%\[
+Q\models{\openrule
+	{
+		\beta_j^{j\in J_Q},
+		 \Pred\,',  
+		\Post\,'}
+	{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
+		\ostate{s_i'^{\, i\in L_Q}}}
+}%\]
+\end{mathpar}
+Then, we have\\[-2ex]
+	\[ P[Q]_{j_0}  
+	\models
+	{\openrule
+		{
+			\beta_j^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
+			\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0},  
+			\Post\uplus \Post\,'}
+		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {\alpha}
+			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
+	}
+	\]
+\end{lemma}
+
+Note that this does not mean that any two pNets can be composed and produce an open 
+transition. Indeed, the predicate $\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0}$ is often not  satisfiable, in particular if the action  $\alpha_Q$ cannot be matched with $\beta_{j_0}$.
+Note also that $\beta_{j_0}$ is  only used as an intermediate term inside formulas in the composed open transition: it 
+does not appear neither as global action nor as an action of a hole.
 
@@
 
-%% \subsection{Post-processing: Elimination of intermediate variables}
-
-%% While building the open transitions, many new variable names are
-%% created, as fresh local variables of synchronisation vectors, and
-%% fresh result variables of intermediate OTs. While these are required
-%% for the semantic construction, they are not significant in the
-%% resulting open automaton. In fact they carry information on the
-%% internal structure of the pNet system, and this information should
-%% \_not\_ be visible when looking at the system as a black box, and in
-%% particular when comparing its behaviour with another system, e.g. by
-%% bisimulation.
-
-%% In the resulting predicate the only significant variables are :\\
-%% - the input variables of pLTS transitions \TODO{heu, non, meme pas, si
-%%   ce sont des comm internes!}\\
-%% - the actions of holes\\
-%% - the result action at toplevel.
-
-%% So we transform the predicates of the resulting OTs, eliminating all
-%% intermediate variables. \TODO{Explain why this should work !! Maybe
-%%   need to be more precise on unification in the matching...}
-
-%\TODO{Eric: full (???) result of the tool execution on the running example on the Simple Prot Spec: Done, on the Counetr version !}
-
-%\begin{figure}[ht]
-%   \centerline{\includegraphics[width=11cm]{ATG/SPSpecOpen}}
-%   \caption{Specification OA}
-%   \label{SimpleProtCounter:SpecOA}
-%\end{figure}
-
-\begin{figure}[ht]
-   \centerline{\includegraphics[width=13cm]{XFIG/SPSpecOpen}}
-   \caption{Specification Open Automaton}
-   \label{SimpleProtCounter:SpecOA}
-\end{figure}
-
-\subsection*{Example}  Figure~\ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the Specification pNet given in Figure \ref{SimpleProt:Spec}. 
-For later references, we give to the transitions of this (strong)
-Specification automaton as $SS_i$ while transitions of the
-Implementation automaton will be labelled $SI_i$. In the figure we
-have annotated each global state with the set of corresponding pLTS variables.
-
- \begin{figure}[ht]
-  \centerline{\includegraphics[width=15cm]{XFIG/SPImplOpen}}
-  \caption{Open Automaton of the Simple Protocol Implementation}  \label{SimpleProtCounter:ImplOA}
-\end{figure}
-
-    Figure \ref{SimpleProtCounter:ImplOA} shows the open automaton of the implementation $SimpleSystem$ (Figure \ref{SimpleProt:Impl}).
-In this drawing, we have short labels for states, representing $\ostate{s_0,m_0,r_0}$ by \texttt{000}.
-Note that open transitions are denoted $\texttt{SI}_i$ and tau open transition by  $\texttt{SI}_{\tau}$.
-The resulting behaviour is quite simple:  we have a main loop including receiving a message from $P$ and transmitting the same message to $Q$, with some intermediate $\tau$ actions from the internal communications between the protocol processes.
-In most of the transitions, you can observe that data is propagated between the successive plts variables (holding the message, and the error counter value).
-On the right of the figure, you have a loop of $\tau$ actions ($\texttt{SI}_4$, $\texttt{SI}_5$ and $\texttt{SI}_6$)  showing the handling of errors and corresponding increments of the error counter.
-
-\subsection{pNet Composition Properties: composition of open transitions}
-The semantics of open pNets allows us to prove two crucial properties relating pNet composition with pNet semantics: open transition of a composed pNet can be decomposed into open transitions of its composing sub-pNets, and conversely, from the open transitions of sub-pNets,  an open transition of the composed pNet can be built.
-
-We start with decomposition: from one open transition of $P[Q]_{j_0}$, we exhibit 
-corresponding behaviours of $P$ and $Q$, and determine the relation between their 
-predicates:
-\begin{lemma}[Open transition decomposition\label{lem-decompose}] Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$}.
-	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose:
-	\[ P[Q]_{j_0}  
-		\models
-		{\openrule
-			{
-				\beta_j^{j\in J}, \Pred,  
-				\Post}
-			{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
-				\ostate{s_i'^{\, i\in L}}}
-		}
-	\]
-		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.
-		 Then there exist $\alpha_Q$, $\Pred\,'$, $\Pred\,''$, 
-		$\Post\,'$, $\Post\,''$ s.t.:\\[-2ex]
-		%\[
-		\begin{mathpar}
-		P\models{\openrule
-			{
-				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
-				\Pred\,',  
-				\Post\,'}
-			{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {\alpha}
-				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
-		}%\]
-	\vspace{-2.2ex}\\\text{and~~}
-		%\[
-		Q\models{\openrule
-			{
-				\beta_j^{j\in J\cap\Holes(Q)}, \Pred\,'',  
-				\Post\,''}
-			{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
-				\ostate{s_i'^{\,i\in L_Q}}}
-		}%\]
-		\end{mathpar}
-		and  $\Pred \iff \Pred\,'
-		\land \Pred\,''\land \alpha_Q=\beta_{j_0}$, $\Post=\Post\,'\uplus 
-		\Post\,''$ where $\Post\,''$ is the restriction of $\Post$ over variables of 
-		$Q$.
-\end{lemma}
-
-Lemma \ref{lem-compose} is combining an open transition of $P$ with
-an open transition of $Q$, and building a corresponding transition of
-$P[Q]_{j_0}$, assembling their predicates.
-
-\begin{lemma}[Open transition composition]\label{lem-compose} 
-	Suppose $j_0\in J$ and:\\[-2ex]
-\begin{mathpar}
-%\[
-P\models{\openrule
-	{
-		\beta_j^{j\in J}, 
-		\Pred,  
-		\Post}
-	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
-		\ostate{s_i'^{\, i\in L}}}
-}%\]
-\text{~~and~~}
-%\[
-Q\models{\openrule
-	{
-		\beta_j^{j\in J_Q},
-		 \Pred\,',  
-		\Post\,'}
-	{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
-		\ostate{s_i'^{\, i\in L_Q}}}
-}%\]
-\end{mathpar}
-Then, we have\\[-2ex]
-	\[ P[Q]_{j_0}  
-	\models
-	{\openrule
-		{
-			\beta_j^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
-			\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0},  
-			\Post\uplus \Post\,'}
-		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {\alpha}
-			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
-	}
-	\]
-\end{lemma}
-
-Note that this does not mean that any two pNets can be composed and produce an open 
-transition. Indeed, the predicate $\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0}$ is often not  satisfiable, in particular if the action  $\alpha_Q$ cannot be matched with $\beta_{j_0}$.
-Note also that $\beta_{j_0}$ is  only used as an intermediate term inside formulas in the composed open transition: it 
-does not appear neither as global action nor as an action of a hole.
-
-\subsection{Bisimulation for open pNets -- a composable bisimulation theory}
+\section{Bisimulation for open pNets -- a composable bisimulation theory}
 \label{section:bisimulation-PN}
@@
 
-\section{Weak bisimulation}\label{sec:weak}
-
-Weak symbolic bisimulation was introduced to relate transition systems
-that have indistinguishable behaviour, with respect to some definition
-of \emph{internal actions} that are considered local to some
-subsystem, and consequently cannot be observed, nor used for
-synchronisation with their context.
-The notion of non-observable actions varies in different contexts,
-e.g. $tau$ in CCS, and $i$ in Lotos, we could define classically a set of
-\emph{internal/non-observable actions} depending on a specific action
-algebra. In this paper, to simplify the notations, we will simply use $\tau$ as the single non-observable action; the generalisation of our results to a set of non-observable actions is trivial. 
-Naturally, a non-observable action cannot be synchronised with
-actions of other systems in its environment. 
-We show here that under such assumption of non-observability of $\tau$ actions, see Definition~\ref{def:Non-ObsTau}, we can define a weak bisimulation relation that is compositional, in the sense of open pNet composition.
-In this section we will first define a notion of weak open transition similar to open transition.
-In fact a weak open transition is made of several open transitions labelled as non-observable transitions, plus potentially one observable open transition.
-This allows us to define weak open automata, and a weak bisimulation relation based on these weak open automata.
-Finally, we apply this weak bisimulation to open pNets, obtain a weak bisimilarity relationship for open pNets, and prove that this relation has compositional properties.
-
-%% \TODO{we should understand if it make sense to distinguish invisible
-%%   from synchronised actions: in the Forte paper we wrote ``using  as 
-%% \emph{invisible actions} a subset of the
-%% \emph{synchronised actions} defined in Section~\ref{section:pnets}''}.
-
-%% Proving bisimulation properties on our hierarchical broadcast example
-%% would take too much space for this paper. Moreover, interesting
-%% properties of the HB example would rather be adequate for weak
-%% bisimulation, and its large state-space would require some
-%% tool-assistance, both for the generation of the open-automata and for
-%% their comparison.
-
-\subsection{Preliminary definitions and notations}
-
-We first specify in terms of open transition, what it means for an action to be non-observable.
-Namely, we constraint ourselves to system where the emission of a $\tau$ action by a sub-pNet cannot be observed by the surrounding pNets.
-In other words, a pNet cannot change its state, or emit a specific observable action when one of its holes emits a $\tau$ action.
-
-More precisely, we state that $\tau$ is not observable if the automaton always allows any $\tau$ transition from holes, and additionally the global transition resulting from a $\tau$ action of a hole is a $\tau$ transition not changing the pNet's state.
-We define $\Id(V)$ as the identity function on the set of variables $V$.
-\begin{definition}[Non-observability of $\tau$ actions for open automata]\label{def:Non-ObsTau}
-An open automaton $A = \mylangle J,\mathcal{S},s_0,V,\mathcal{T}\myrangle$ \emph{cannot observe $\tau$ actions} if and only if for all $j$ in $J$ and $s$ in $\mathcal{S}$ we have:
-\begin{enumerate}
-\item
-\[ \openrule
-         {
-           (j\mapsto\tau),\True,\Id(V)}
-         {s \OTarrow {\tau} s}
-         \in \mathcal{T}
-\]
-and 
-\item for all $\beta_j$, $J$,  $\alpha$,  $s$, $s'$, $\Pred$, $\Post$  such that
-\[ \openrule
-         {
-           \beta_j^{j\in J},\Pred,\Post}
-         {s \OTarrow {\alpha} s'}
-         \in \mathcal{T} \] If there exists $j$ such that $\beta_j=\tau$ then we have: \[ \alpha=\tau\land s=s'\land \Pred=\True\land\Post=\Id(V) \land J=\{j\}
-\]
-\end{enumerate}
-\end{definition}
-The first statement of the definition states that the open automaton must allow a hole to do a silent action at any time, and must not observe it, i.e.
-cannot change its internal state because a hole did a $\tau$ transition.
-The second statement ensures that there cannot be in the open automaton other transitions that would be able to observe a $\tau$ action from a hole.
-The condition $J=\{j\}$ is a bit restrictive, it could safely be replaced by $\forall j\in J.\, \beta_j=\tau$, allowing the other holes to perform $\tau$ transitions too (because these $\tau$ actions cannot be observed).
-
-By definition, one weak open transition contains  several open transitions, where  each open transition can require an observable action from a given hole, the same hole might have to emit several observable actions for a single weak open transition to occur.
-Consequently, for a weak open transition to trigger, a sequence of actions from a given hole may be required.
-
-Thus, we let $\gamma$ range over sequences of action terms and use $\dotcup$ as the concatenation operator that appends sequences of action terms: given two sequences of action terms  $\gamma\dotcup\gamma '$ concatenates the two sequences.
-The operation is lifted to indexed sets of sequences:   at each index $i$, $\set {\gamma_1}\dotcup \set {\gamma_2}$ concatenates the sequences of actions at index $i$ of $\set{\gamma_1}$ and the one at index $i$ of $\set {\gamma_2}$\footnote{One of the two sequences is empty when $i\not \in \dom(\set{\gamma_1})$ or $i\not \in \dom(\set{\gamma_2})$ .}.
-$[a]$ denotes a sequence with a single element.
-
-As required actions are now sequences of observable actions, we need an operator to build them from set of actions that occur in open transitions, i.e.
-an operator that takes a set of actions performed by one hole and produces a sequence of observable actions.
-
-Thus we define $\vis{\set\beta}$ as the mapping $\set\beta$  with only observable actions of the holes in $I$, but where each element is either empty or a list of length 1:
- \[\vis{\beta_i^{i\in I}} = [\beta_i]^{i\in I'}\text{ where }I'=\left\{i| i\in I \land \beta_i\neq \tau\right\}\]
-
-As an example the $\vis{\set\beta}$ built from the transition $OT_1$ in Example~\ref{OT:SimpleProt}, page \pageref{OT:SimpleProt} is $\texttt{P}\mapsto [\texttt{p-send(m)}]$.
-Remark that in our simple example no $\tau$ transition involves any visible action from a hole, so we have no $\beta$ sequences of length longer than 1 in the weak automaton.
-%\TODO{en fait c'est faux ! les boucles SS\_1, SS\_2, WS\_1, WS\_2 sont aussi valides avec p\_a ou q\_b = tau, donc on peut avoir des sequences de longueur arbitraire d'actions de P et de Q}
-
-\subsection{Weak open transition definition}
-
-Because of the non-observability property (Definition~\ref{def:Non-ObsTau}), it is possible to add any number of $\tau$ transitions of the holes before or after any open transition freely.
-This property justifies the fact that we can abstract away $\tau$ transitions from holes in the definition of a weak open transition.
-
-%
-%Classically, we start by defining a derived transition relation based
-%on sequences of invisible actions.
-
-\def\InvAct{\mathcal{Inv}}
-%
-%\RAB{We let $\gamma$ range over words (of action terms) and use $\dotcup$ as the union that appends words.}
-
-\begin{definition}[Weak open transition (WOT)]\label{def:weakOT}
-A weak open transition over a
-	set $J$ of holes with sorts $\Sort_j^{j\in J}$ and a set of states $\mathcal{S}$ is 
-	a structure of the form:	
-\begin{mathpar}
- \openrule
-         {
-           \gamma_j^{j\in J'},\Pred,\Post}
-         {s \OTWeakarrow {\alpha} s'}
- \end{mathpar}
-	Where $J'\subseteq J$, $s, s'\in\mathcal{S}$ and $\gamma_j$
-        is a list of transitions of the hole $j$, with each element of the list in $\Sort_j$. $\alpha$ is an action 
-        label denoting the resulting action
-        of this open transition. \Pred\ and \Post\ are defined similarly to Definition~\ref{def:OT}. We use $\WT$ to range over sets of weak open transitions.
-
-A weak open automaton $\mylangle J,\mathcal{S},s_0,V,\WT\myrangle$ is similar to an open automaton  except that $\WT$ is a set of weak open transitions over $J$ and $\mathcal{S}$.
-\end{definition}
-
-A weak open transition labelled $\alpha$ can be seen as a sequence of open transitions that are all labelled $\tau$ except one that is labelled $\alpha$; however conditions on predicates, effects, and states must be verified for this sequence to be fired.
-
-We are now able to build a weak open automaton from an open automaton.
-This is done in a way that resembles the process of $\tau$ saturation: we add  $\tau$ open transitions before or after another (observable or not) open transition.
-\begin{definition}[Building a weak open automaton]\label{def:buildweakOT}
-  Let $A = \mylangle J,\mathcal{S},s_0,V,\mathcal{T}\myrangle$ be an open automaton. 
-The weak open automaton \emph{derived} from $A$ is an open automaton  $\mylangle J,\mathcal{S},s_0,V,\WT\myrangle$ where $\WT$ is derived from $\mathcal{T}$ by saturation, applying the following rules:
-%\noindent{\bf Invisible $\tau$ transitions:}
-\begin{mathpar}
- \openrule
-         {
-           \emptyset,\symb{True},\Id(V)}
-         {s \OTWeakarrow {\tau} s} \in \WT  \qquad \WTUn
- \end{mathpar}
-and
-\begin{mathpar}
-\inferrule{
- \openrule
-         {
-           \set{\beta},\Pred,\Post}
-         {s \OTarrow {\alpha} s'} \in \mathcal{T}
-} 
-{ \openrule
-         {
-           \vis{\set{\beta}}\!,\Pred,\Post
-				 } {s \OTWeakarrow {\alpha} s'} \in \WT
-}\qquad \WTDeux
-%\inferrule{
-% \openrule
-%         {
-%           \set{\beta},\Pred,\Post}
-%         {s \OTarrow {\tau} s'} \in \mathcal{T}
-%\\
-% \openrule
-%         {
-%           \set{\gamma},\Pred\,',({x_k\gets e_k})^{k\in K}   }
-%         {s' \OTWeakarrow {\tau} s''} \in \WT
-%}
-%{ \openrule
-%         {
-%           \vis{\set{\beta}}\dotcup\set{\gamma},\Pred\land\Pred\,'\subst{\Post\,},
-%				({x_k\gets (e_k\subst{\Post\,})})^{k\in K} } 
-%         {s \OTWeakarrow {\tau} s''} \in \WT
-%}
- \end{mathpar}
- and
-%\noindent{\bf Other transitions:}
-\begin{mathpar}
-\inferrule {\openrule
-         {
-           \set{\gamma_1},\Pred_1,\Post_1   }
-         {s \OTWeakarrow {\tau} s_1} \in \WT
-\qquad
-\openrule
-         {
-           \set{\gamma_2},\Pred_2,\Post_2  }
-         {s_1 \OTWeakarrow {\alpha} s_2} \in \WT
-\qquad
-\openrule
-         {
-           \set{\gamma_3},\Pred_3,\Post_3  }
-         {s_2 \OTWeakarrow {\tau} s'} \in\WT
-\\
-\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land \Pred_3\subst{\Post_2\shortotimes\Post_1}
-\\
-\set{\gamma}=\set{\gamma_1}\dotcup \set{\gamma_2}\subst{\Post_1}\dotcup\set{\gamma_3}\subst{\Post_2\shortotimes \Post_1}\\
-\alpha'=\alpha\subst{\Post_1}
-}
-{
-\openrule
-         {\set{\gamma}
-           ,
-		\Pred,
-				\Post_3\shortotimes\Post_2\shortotimes\Post_1} 
-         {s \OTWeakarrow {\alpha'} s'} \in\WT
-} \WTTrois
-\end{mathpar}
-
-\end{definition}
-Rule $\WTUn$ states that it is always possible to do a non-observable transition, where the state is unchanged and the holes perform no action.
-Rule~$\WTDeux$ states that each open transition can be considered as a weak open transition.
-The last rule is the most interesting:  Rule~$\WTTrois$ allows any number of $\tau$ transitions before or after any weak open transition.
-This rules carefully composes predicates, effects, and actions of the holes, indeed in the rule, predicate $\Pred_2$ manipulates variables of $s_1$ that result from the first weak open transition.
-Their values thus depend on the initial state but also on the effect (as a substitution $\Post_1$) of the first weak open transition.
-In the same manner, $\Pred_3$ must be applied the joint substitution $\Post_2\shortotimes\Post_1$.
-Similarly, effects on variables must be applied to obtain the global effect of the composed weak open transition, it must also be applied to observable actions of the holes, and to the global action of the weak open transition.
-
-%% \begin{figure}[ht]
-%%    \centerline{\includegraphics[width=12cm]{ATG/WOT1}}
-%%   \caption{Construction of the Weak Open transition WOT1}
-%%    \label{WOT1}
-%% \end{figure}
-
-%% \begin{figure}[ht]
-%%    \centerline{\includegraphics[width=11cm]{ATG/WOT2}}
-%%   \caption{Construction of WOT2}
-%%    \label{WOT2}
-%% \end{figure}
-
-\begin{figure}[ht]
-   \centerline{\includegraphics[width=13cm]{XFIG/WOT2-result}}
-  \caption{Construction of an example of weak open transition}
-   \label{WOT2}
-\end{figure}
-
-\begin{example} [A weak open-transition]
-Figure \ref{WOT2} shows the construction of one of the weak transitions of the Specification OA.
-On the top we show the subset of the original open automaton (from Figure \ref{SimpleProtCounter:SpecOA}) considered here, and at the bottom the generated weak transition.
-For readability, we abbreviate the weak open transitions encoded by $\openrule   {\{\}, True,	() } {s \OTWeakarrow \tau s'}$  as $W_\tau$.
-The weak open transition shown here is the transition delivering the result of the algorithm to hole $Q$ by applying rules: \WTUn,\WTDeux, and \WTTrois.
-First rule \WTUn~ adds a $WT_\tau$ loop on each state.
-Rule \WTDeux~ transforms each 3 OTs into WOTs.
-Then consider application of Rule \WTTrois~ on a sequence 3  WOTs.
-$\openrule
-         {\{\}, True,
-			(\texttt{b\_ec}\gets \texttt{b\_ec}+1) }
-         {\texttt{b1}\OTWeakarrow \tau \texttt{b1}}$; $\openrule
-         {\{\}, True,
-			(\texttt{b\_ec}\gets \texttt{b\_ec}+1) }
-         {\texttt{b1} \OTWeakarrow \tau \texttt{b1}}$;  $\openrule
-         {\{\}, True,
-			() }
-         {\texttt{b1} \OTWeakarrow \tau \texttt{b1}}$. Then Rule \WTTrois~ produces  $\openrule
-         {\{\}, True,
-			(\texttt{b\_ec}\gets \texttt{b\_ec}+2) }
-         {\texttt{b1} \OTWeakarrow \tau \texttt{b1}}$. We can iterate this construction an arbitrary number of times, getting for any natural number $n$ a weak open transition:
-  $\openrule
-         {\emptyset, True,
-			(\texttt{ec}\gets \texttt{ec}+n) }
-        {\texttt{b1} \OTWeakarrow \tau \texttt{b1}}\, \forall n \geq 0$.
-Finally,  applying again \WTTrois, and using the central open transition having \texttt{\nounderline{out(b\_msg,b\_ec)}}  as $\alpha$, we get the resulting weak open transition between b1 and b0 (as shown in Figure \ref{WOT2}).
-Applying the substitutions finally yields the weak transitions family $WS_7$ in Figure  \ref{SimpleProtCounter:WeakSpecOA}.
-
- %     $\openrule
- %        {\{\texttt{Q}\mapsto\texttt{q-revc(ec)}\subst{ec\gets ec+n}\}, True,
-%			(\texttt{ec}\gets \texttt{ec}+n) }
- %        {b1 \OTWeakarrow {\nounderline{\texttt{out(m,ec)}}\subst{ec\gets ec+n}} b0} \forall n \geq 0$. 
-\end{example}
-
-  \begin{example}[Weak open automata]
-    Figures \ref{SimpleProtCounter:WeakSpecOA} and \ref{SimpleProtCounter:ImplWOA2} respectively show the weak automata of the simple protocol specification and implementation.
-We encode weak open transitions  by $WS$ on the specification model and by $WI$ on the implementation model.
-
-\begin{figure}[h]
-   \centerline{\includegraphics[width=15cm]{XFIG/SPSpecWeakOpen}}
-  \caption{Weak Open Automaton of the Specification}
-   \label{SimpleProtCounter:WeakSpecOA}
-\end{figure}
-
- For readability, we do not include the full details of the Implementation weak open transitions in Figure \ref{SimpleProtCounter:ImplWOA2}, but we show some examples below and the full list is included in Appendix \ref{Appendix:FullExample}.
-First, let us point out that the weak OT loops ($WI_1$,$WI_2$ and $W_\tau$) on state ${000}$ are also present in all other states, we did not repeat them.
-Then many WOTs are similar, and numbered accordingly as 3, 3a, 3b, 3c and 8, 8a, 8b, 8c respectively: they only differ by their respective source or target states; the "variant" WOTs appear in blue in   Figure \ref{SimpleProtCounter:ImplWOA2}.
-\end{example}
-
-%\begin{figure}[h]
-  % \centerline{\includegraphics[width=11cm]{XFIG/SimpleProtImpl-WOA}}
- % \caption{Weak Open Automaton of the implementation}
- %  \label{SimpleProtCounter:ImplWOA}
-%\end{figure}
-
-\begin{figure}[h]
-   \centerline{\includegraphics[width=11cm]{XFIG/SimpleProtImpl-WOA2}}
-  \caption{Weak Open Automaton of the implementation}
-   \label{SimpleProtCounter:ImplWOA2}
-\end{figure}
-
-Now let us give some details about the construction of the weak automaton of the implementation pNet, obtained by application of the weak rules as explained above.
-We concentrate on weak open transitions $WI_3$ and $WI_4$.
-Let us denote as $post_n$ the effect (substitution) of the strong open transitions $SI_n$ from Figure \ref{SimpleProtCounter:ImplOA}:
-\smallskip
-
-$post_3 = (\texttt{s\_msg}\gets \texttt{m}, \texttt{s\_ec}\gets 0)$
-
-$post_4 = (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec})$
-
-$post_5 = ()$
-
-$post_6 = (\texttt{s\_ec}\gets \texttt{s\_ec+1})$
-
-\medskip
-
-Then the effect of one single $100 \xrightarrow{OT_4} 210 \xrightarrow{OT_5} 220 \xrightarrow{OT_6} 100$ loop is\footnote{when showing  the result of $Posts$ composition, we will omit the identity substitutions introduced by the $\shortotimes$ definition in page \pageref{def:substitutions}}:
-\[post_{456} = post_6 \shortotimes\ post_5 \shortotimes\ post_4
-= (\texttt{s\_ec}\gets \texttt{s\_ec}+1)\]
-
-So if we denote ${post_{456*}}$ any iteration of this loop, we get ${post_{456*}} = (\texttt{s\_ec}\gets \texttt{s\_ec}+n)$ for any $n\ge 0$, and the \Post~ of the weak OT  $WI_{3}$ is:\\
- $Post_3 = post_{456*}\shortotimes\ post_3 = (\texttt{s\_msg}\gets m, \texttt{s\_ec}\gets n), \forall n\ge 0$ and \Post~ of  $WI_{3a}$  is:\\ $post_4\shortotimes {post_{456*}}\shortotimes\ post_3 = (\texttt{m\_msg}\gets m, \texttt{m\_ec}\gets n), \forall n\ge 0$.
-\medskip
-
-We can now show some of the weak OTs of Figure \ref{SimpleProtCounter:ImplWOA2} (the full table is included in Appendix \ref{Appendix:FullExample}).
-As we have seen above, the effect of rule $WT_3$ when a silent action have an effect on the variable $ec$ will generate an infinite family of WOTs, depending on the number of iterations through the loops.
-We denote these families using a "meta-variable" $n$, ranging over $\mathcal{N}$.
-% \TODO{Qu'est-ce qu'on avait dit ici pour "$n$" ? a droite ou a gauche, mais pas les deux ?Et est-ce qu'on le laisse en italique dans les expressions, pour souligner son statut de parametre ?.
-% Dans tous les cas expliquer ?}
-\smallskip
-
-$ WI_1 = \openrule
-{\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{x}. \texttt{p-a} \neq \texttt{p-send(x)} ], ()}
-{s \OTWeakarrow {\texttt{p-a}} s}
-$ (for any  $s \in S$)
-
-$ \forall n\ge 0.\, WI_3(n) = \openrule
-  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
-    (\texttt{s\_msg}\gets \texttt{m}, \texttt{s\_ec}\gets n)}
-  {000 \OTWeakarrow {\nounderline{\texttt{in(m)}}} 100}
-        $
-
-$  \forall n\ge 0.\, WI_4(n) = \openrule
-         {\{\}, True, 
-   (\texttt{m\_msg}\!\gets\! \texttt{s\_msg}, \texttt{m\_ec}\!\gets\! \texttt{s\_ec}+n, \texttt{s\_ec}\!\gets\! \texttt{s\_ec}+n)}
-         {100 \OTWeakarrow {\tau} 210}
-        $
-
-$  \forall n\ge 0.\, WI_{456}(n) = \openrule
-         {\{\}, True, 
-    (\texttt{s\_ec}\gets \texttt{s\_ec}+n)}
-  {100 \OTWeakarrow {\tau} 100}
-        $
-
-   \medskip     
-The  \Post~of the weak OT $ WI_{6a}$ is:
-$$
-\begin{array}{l@{}l}
-Post_{6a}&= post_{4}\shortotimes\ post_{456*}\shortotimes\ post_{6}\\ 
-&=  (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec})\,
-\shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+n) 
-\shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+1) \\
-&= (\texttt{m\_msg}\!\gets \texttt{s\_msg}, \texttt{m\_ec}\!\gets \texttt{s\_ec}+1\!+\!n, \texttt{s\_ec}\!\gets \texttt{s\_ec}+1\!+\!n)
-\end{array}
-$$
-
-So we get:
-
-$ \forall n\ge 0.\, WI_{6a}(n) = \openrule
-         {\{\}, True, 
-         (\texttt{m\_ec}\gets \texttt{s\_ec}+1+n, \texttt{s\_ec}\gets \texttt{s\_ec}+1+n)}
-         {220 \OTWeakarrow {\tau} 210}$
-
-%\begin{align*}
-%\\Post_{8c}=& post_{8}\shortotimes\ post_{7}\shortotimes\ post_{4}\shortotimes\ post_{456*} 
-%= (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_msg}+1+n), \forall n\ge 0\\ 
-%WI_{8c}(n) =& \openrule
-  %       {\{\texttt{Q}\mapsto \texttt{q-recv(s\_msg,s\_ec}+n)\}, True, (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_msg}+1+n)}
-   %      {210 \OTWeakarrow {\nounderline{\texttt{out(s\_msg,s\_ec}+n)}} 202}\forall n\ge 0
-%\end{align*}
-
-\subsection{Composition properties: composition of weak open transitions}
-We now have two different semantics for open pNets: a strong semantics, defined  as an open automaton, and as a weak semantics, defined as a weak open automaton.
-Like the open automaton, the weak open automaton features valuable composition properties.
-We can exhibit  a composition property and a decomposition property that relate open pNet composition with their semantics, defined as weak open automata.
-These are however technically more complex than the ones for open automata because each hole performs a set of actions, and thus a composed transition is the composition of one transition of the top-level pNet and a sequence of transitions of the sub-pNet that fills its hole.
-They can be found as Lemmas~\ref{lem-decomposeWOT}, Lemma~\ref{lem-Weakcompose1}, and Lemma~\ref{lem-Weakcompose} in Appendix~\ref{sec:app-composition}.
-
-\subsection{Weak FH-bisimulation}
-For defining a bisimulation relation between weak open automata, two options are possible.
-Either we define a simulation similar to the strong simulation but based on open automata, this would look like the FH-simulation but would need to be adapted to weak open transitions.
-Or we define directly and classically a weak FH-simulation as a relation between two open automata, relating the open transition of the first one with the transition of the weak open automaton derived from the second one.
-
-The definition below specifies how a set of weak open transitions can simulate an open transition, and under which condition; this is used to relate, by weak FH-bisimulation, two open automata by reasoning on the weak open automata that can be derived from the strong ones.
-This is defined formally as follows.
-
-\begin{definition}[Weak FH-bisimulation]\label{def-Weak-bisim} ~\\
-\noindent
-Let $A_1 = \mylangle J,\mathcal{S}_1, s_0,V_1,
-    \mathcal{T}_1\myrangle$ and $A_2 = \mylangle J,\mathcal{S}_2,t_0, V_2, \mathcal{T}_2\myrangle$ be open automata with disjoint sets of variables.
-Let $\mylangle J,\mathcal{S}_1, s_0,V_1,
-    \WT_1\myrangle$ and $\mylangle J,\mathcal{S}_2,t_0, V_2, \WT_2\myrangle$ be the
-weak open automata derived from $A_1$ and $A_2$ respectively.
-Let $\mathcal{R}$ a relation over
-$\mathcal{S}_1$ and $\mathcal{S}_2$, as in Definition~\ref{def-FH-bisim}.
-
-Then 
-   $\mathcal{R}$ is a weak FH-bisimulation iff for any  states
-$s\in\mathcal{S}_1$ and
-$t\in\mathcal{S}_2$ such that $(s,t|\Pred)\in\mathcal{R}$, we 
-   have the following:
-
- \begin{itemize}
- \item  For any open transition $OT$ in $\mathcal{T}_1$:
- \begin{mathpar}
-     \openrule
-         {
-           \beta_j^{j\in J'},\Pred_{OT},\Post_{OT}}
-         {s \OTarrow {\alpha} s'}
-
-\end{mathpar}
- there exist weak open transitions $\symb{WOT}_x^{\;x\in X} \subseteq \WT_2$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {t \OTWeakarrow {\alpha_x} t_x}
-\end{mathpar}
- such that  $\forall x.\, \{j\in J'|\beta_j\neq\tau\}=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
- and  \\
- $\Pred \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
-   \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
-     \!\land\! \alpha\!=\!\alpha_x\! \land\!  
-     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}$
-
- \item  and symmetrically any open transition from $t$ in $\mathcal{T}_2$ can be 
-      covered by a set of weak transitions from $s$ in $\WT_1$.
- \end{itemize}
-
-Two pNets are weak FH-bisimilar if there exists a relation between their associated 
-automata that is a Weak FH-bisimulation and their initial states are in the relation, i.e. 
-the predicate associated to the relation between the initial states is \True.
- \end{definition}
-
-Compared to strong bisimulation, except the obvious use of weak open transitions to simulate an open transition, the condition on predicate is slightly changed concerning actions of the holes.
-Indeed only the visible actions of the holes must be compared and they form a list of actions, but of length at most one.
-
-Our first important result is that Weak FH-bisimilarity is an equivalence in the same way as strong FH-bisimilarity:
-
-\begin{theorem}[Weak FH-Bisimulation is an equivalence]\label{thm-weak-equiv} Suppose $\mathcal{R}$ 
-is a weak FH-bisimulation. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
-reflexive, symmetric and transitive.
-\end{theorem}
-The proof  is detailed in Appendix \ref{app-WFH-equiv}, it follows a similar pattern as the proof that strong FH-bisimulation is an equivalence, but technical details are different, and in practice we rely on a variant of the definition of weak FH-bisimilarity; this equivalent version simulates a \emph{weak} open transition with a set of weak open transition.
-The careful use of the best definition of weak FH-bisimilarity makes the proof similar to the strong FH-bisimulation case.
-
-\subsubsection*{Proving bisimulation in practice}
-
-In practice, we are dealing with finite representations of the (infinite) open automata.
-In \cite{hou:hal-02406098}, we defined a slightly modified definition of the ``coverage'' proof obligation, in the case of strong FH-Bisimulation.
-This modification is required to manage in a finite way all possible instantiations of an OT.
-In the case of weak FH-Bisimulation, the proof obligation from Definition \ref{def-Weak-bisim} becomes:
-      \begin{multline*}
-\forall fv_{OT}.\, \Big\{ \Pred \land \Pred_{OT} \implies\\
- \bigvee_{x\in X}\!
-  \left[\exists fv_{OT_x}.
-    \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
-     \!\land\! \alpha\!=\!\alpha_x\! \land\!  
-     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)\right]\Big\}
-\end{multline*}
-
-In which $fv_{OT}$ denotes the set of free variables of all expressions in $OT$.
-\subsection{Weak bisimulation for open pNets}
+\section{Weak bisimulation for open pNets}
 
@@
 From the definition of the weak open automata of pNets, we can now study the properties of weak bisimulation concerning open pNets.
-
-\subsection{Properties of weak bisimulation for open pNets}
+\section{Properties of weak bisimulation for open pNets}
 
@@
 
-\subsubsection*{Running example}
-\label{subsubsection:runnig example}
-In Section~\ref{sec:weak} we have shown the full satured weak automaton for both the specification and the implementation of the simple protocol.
-We will show here how we can check if some given relation between these two automata is a weak FH-Bisimulation.
-
-\medskip
-\noindent
-Preliminary remarks:
-  \begin{itemize}
-    \item Both pNets trivialy verify the ``non-observability''
-      condition: the only vectors having $\tau$ as an action of a
-      sub-net are of the form ``$< -, \tau, -> \rightarrow \tau$''.
-    \item We must take care of variable name conflicts: in our example, the variables of the 2 systems already have different names, but the action parameters occurring in the transitions (\texttt{m}, \texttt{msg}, \texttt{ec}) are the same, that is not correct.
-In the tools, this is managed by the static semantic layer; in the following example, we have renamed all conflicting variables with 1 for the Spec, and 2 for the Impl.
-    \end{itemize}
-
-  \medskip
-  Now consider the relation $\mathcal{R}$ defined by the following triples:
-
-  \begin{tabular}{|c|c|l|}
-\hline
-    Spec state & Impl state & Predicate\\
-    \hline
-    b0 & $000$ & True\\
-    b0 & $202$ & True\\
-    b1 & $100$ & $\texttt{b\_msg = s\_msg} \land \texttt{b\_ec = s\_ec}$\\
-    b1 & $210$ & $\texttt{b\_msg = m\_msg} \land \texttt{b\_ec = m\_ec}$\\
-    b1 & $220$ & $\texttt{b\_msg = s\_msg} \land \texttt{b\_ec = s\_ec}$\\
-    b1 & $201$ & $\texttt{b\_msg = r\_msg} \land \texttt{b\_ec = r\_ec}$\\
-    \hline
-    \end{tabular}
-
-  \medskip
-  Checking that $\mathcal{R}$ is a weak FH-Bisimulation means checking, for each of these triples, that each (strong) OT of one the states corresponds to a set of WOTs of the other, using the conditions from Definition \ref{def-Weak-bisim}.
-  We give here one  example: consider the second triple from the table, and transition $SS_3$ from state \texttt{b0}. Its easy to guess that it will correspond to $WI_3(0)$ of state $202$.
-
-  $ SS_3 = \openrule
-  {\{\texttt{P}\mapsto \texttt{p-send(m1)}\}, True,
-    (\texttt{b\_msg}\gets \texttt{m1}, \texttt{b\_ec}\gets 0)}
-  {\text{b0} \OTarrow {\nounderline{\texttt{in(m1)}}} \text{b1}}
-  $
-
-$ WI_3(0) = \openrule
-  {\{\texttt{P}\mapsto \texttt{p-send(m2)}\}, True,
-    (\texttt{s\_msg}\gets \texttt{m2}, \texttt{s\_ec}\gets 0)}
-  {000 \OTWeakarrow {\nounderline{\texttt{in(m2)}}} 100}
-  $
-
-  Let us check formally the conditions:
-
-\begin{itemize}
-  \item Their sets of active (non-silent) holes is the same: $J' = J_x = \{\texttt{P}\}$.
-  \item Triple ($\text{b1},  100,  \texttt{b\_msg = s\_msg} \land \texttt{b\_ec = s\_ec}$) is in $\mathcal{R}$.
-  \item The verification condition \\
-    $\forall fv_{OT}.\, \{ \Pred \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
-   \left[\exists fv_{OT_x}.
-  \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
-     \!\land\! \alpha\!=\!\alpha_x\! \land\!  
-     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\!\Post_{OT_x}}\right)\right]\}}$
-
-\medskip Gives us:
-
-$\forall \texttt{m1}.\, \{True \land True\hspace{3mm} \implies
-\exists \texttt{m2}. \\
-(\texttt{[p-send(m1)]} = \texttt{[p-send(m2)]}
-\land True
-\land \nounderline{\texttt{in(m1)}} = \nounderline{\texttt{in(m2)}} \land 
-\\
-(\texttt{b\_msg\!\!
-= \!\!s\_msg} \land \texttt{b\_ec\!\!
-=\!\!
-s\_ec}) \subst{(\texttt{b\_msg}\!\gets\!
-\texttt{m1}, \texttt{b\_ec}\!\gets\!
-0)\uplus (\texttt{s\_msg}\!\gets\!
-\texttt{m2},\texttt{s\_ec}\!\gets\!
-0)})\}$
-
-\medskip That is reduced to:
-
-$\forall \texttt{m1}. \exists \texttt{m2}.\,
-(\texttt{p-send(m1)} = \texttt{p-send(m2)}
-\land \texttt{in(m1)} = \texttt{in(m2)}
-\land \texttt{m1}=\texttt{m2} \land 0=0)$
-
-\medskip That is a tautology.
-
-\end{itemize}
-
-\section{Related Works}\label{sec:RW}
-
- To the best of our knowledge, there are not many research works on Weak Bisimulation Equivalences between such complicate system models (open, symbolic, data-aware, with loops and assignments).
-We give a brief overview of other related publications, focussing first on Open and Compositional approaches, then on Symbolic Bisimulation for data-sensitive systems.
-
-%\TODO{Logique de reorganisation: 1: Open et compositionel [15,13, peut-etre 17], 2: symbolic et data-sensitive [lin, rathke 4 et ?, 5, puis Lotos 18, Pi-calc 16,19,20,22, quantum 25.]}
-
-\subsubsection*{Open and Compositional systems}
-%\TODO{retravailler le paragraphe ci dessous: faire ref a Facs-2013 (reconfig ds pNets) - virer 14 (probabilistic) ?} \cite{GasparHM:2013}
-In
-\cite{Johnson:2013:CBSE,Johnson:2014:qosa}, the authors investigate several methodologies for the compositional verification of software systems, with the aim to verify reconfigurable component systems.
-To improve scaling and compositionality, the authors  decouple the verification problem that is to be resolved by a SMT (satisfiability modulo theory) solver into independent sub-problems on independent sets of variables.
-These works clearly highlight the interest of incremental and compositional verification in a very general setting.
-In our own work on open pNets, adding more structure to the composition model, we show how to enforce a compositional proof system that is more powerful than independent sets of variables.
-Our theory has also been encoded into an SMT solver and it would be interesting to investigate how the examples of evolving systems studied by the authors could be encoded into pNet and verified by our framework.
-However, the models of Johnson et al.
-are quite different from ours, in particular they are much less structured, and translating them is clearly outside the scope of this article.
-In previous work \cite{gaspar:hal-00916115}, we also have shown how (closed) pNet models could be used to encode and verify finite instances of reconfigurable component systems. 
-%Additionally, the more compositional constraint resolution provided by the authors could also be interesting to make our SMT proofs scale better (inside a single pNet for example), the integration of the Z3 framework described in \cite{Johnson:2014:qosa} with our proof theory for open pNets would also be worth investigating from a practical point of view.
-%One major different however is that pNets in their current state are not much adapted to probabilistic verification contrarily to \cite{Johnson:2014:qosa} but they are better suited to verify complex behavioural properties.
-
-%\TODO{Et ou on place celui-la:  https://www.researchgate.net/publication/322674459\_Bisimulations\_on\_Data\_Graphs ? }
-
-Methodologies for reasoning about abstract semantics of open systems can be found in \cite{BaldanBB:2002, BaldanBB:07,Dubut:20}, authors introduce  behavioural equivalences for open systems from various symbolic approaches.
-Working in the setting of process calculi, some close relations  exist with the work  of the authors of \cite{BaldanBB:2002,BaldanBB:07}, where both approaches are based
-on some kinds of labelled transition systems.
-The distinguishing feature of their approach is the transitions systems are labelled with logical formulae that provides  an abstract characterisation of the structure that a hole must possess and of the actions it can perform in order to allow a transition to fire.
-Logical formulae are suitable formats that capture the general class of components that can act as the placeholders of the system during its evolution.
-In our approach we purposely leave the algebra of action terms undefined but the only operation we allow on action of holes is the comparison with other actions.
-Defining properly the interaction between a logical formulae in the action and the logics of the pNet composition seems very difficult.
-
-\subsubsection*{Symbolic and data-sensitive systems}
- As mentioned in the \emph{Introduction}, the work that brought us a lot of inspirations are those of Lin et al.
-\cite{IngolfsdottirL:2001,HennessyLin:TCS95,Linconcur96}.
-They developed the theory of symbolic transition graphs (STG), and the associated symbolic (early and late, strong and weak) bisimulations, they also study STGs with assignments as a model for message-passing processes.
-Our work extends these in several ways: first our models are compositional, and our bismulations come with effective conditions for being preserved by pNet composition (i.e.
-congruent), even for the weak version.
-This result is more general than the bisimulation congruences for value-passing CCS in \cite{IngolfsdottirL:2001}.
-Then our settings for management of data types are much less restrictive, thanks to our use of satisfiability engines, while Lin's algorithms were limited to data-independent systems.
-
-In a similar way, \cite{Abriola:2018} presents a notion of ''data-aware'' bisimulations on data graphs, in which computation of such bisimulations is studied based on XPath logical language extended with tests for data equality.
-
-%Lin present a symbolic bisimulation between symbolic transition graph with assignments (STGA), as mentioned in \emph{Introduction}, bring us lots of inspirations.
-
-Research related to the keyword "Symbolic Bisimulation" refer to two very different domains, namely BDD-like techniques for modelling and computing finite-state bisimulations, that are not related to our topic; and symbolic semantics for data-dependant or high-order systems, that are very close in spirit to our approach.
-In this last area, we can mention
-Calder's work \cite{calder2001symbolic}, that  defines a symbolic semantic for full LOTOS, with a symbolic bisimulation over it;
-Borgstrom et al., Liu et al, Delaune et al.
-and Buscemi et al.
-providing symbolic semantic and equivalence for different variants of pi calculus respectively \cite{borgstrom2004symbolic,delaune2007symbolic,liu2010complete,buscemi2008open}; and more recently
- Feng et al. provide a symbolic bisimulation for quantum processes \cite{feng2014symbolic}.
-All the above works, didn't give a complete approach for verification, and the models on which these works based are definitely different from ours.
-
-% Another line of research is devising the algorithm for computing symbolic Bisimulation Equivalence.
-% In Dovier's work, they provide a rank-based algorithm, layering the input model to compute bisimulation\cite{dovier2002rank}. 
-% Baldan et al. also focus on open systems, using a logical programming language \emph{Prolog} to model the systems and compute Bisimulation\cite{baldan2001compositional}.
-%Wimmer et al. present a signature-based approach to compute Bisimulation, implemented by using BDDs\cite{wimmer2006sigref}.
-
-\section{Conclusion and Discussion}
-\label{section:conclusion}
- pNets (Parameterised Networks of Automata) is a formalism adapted to the representation of the behaviour of a parallel or distributed systems.
-One  strength of pNets is their parameterised nature, making them adapted to the representation of systems of arbitrary size, and making the modelling of parameterised system possible.
-Parameters are also crucial to reason on interaction protocols that can address one entity inside an indexed set of processes.
-pNets have been successfully used to represent behavioural specification of parallel and distributed components and verify their correctness~\cite{AmeurBoulifa2017,HKM-FASE16}.
-VCE is the specification and verification platform that uses pNets as an intermediate representation.
-
-Open pNets are pNets with holes; they are adapted to represent processes parameterised by the behaviour of other processes, like composition operators or interaction 
-protocols that synchronize the actions of processes that can be plugged afterwards. Open
-pNets are hierarchical composition of automata with holes and parameters. We
-defined here a semantics for open pNets and a complete bisimulation theory for them. 
-The semantics of open pNets relies on the definition of open automata that are automata with holes and parameters, but no hierarchy.
-Open automata are somehow labelled transition systems with parameters and holes, a notion that is useful to define semantics, but makes less sense when modelling a system, compared to pNets.
-To be precise, it is on open automata that we define our bisimulation relations.
-
-This article defines a strong and a weak bisimulation principles that are adapted to parameterised systems and hierarchical composition.
-Our bisimulation principle handles pNet parameters in the sense that two states might be or not in relation depending on the value of parameters.
-Our strong  bisimulation is compositional by nature in the sense that bisimulation is maintained when composing processes.
-We also identified a simple and realistic condition on the semantics of non-observable actions that allows weak bisimulation to be also compositional.
-Overall we believe that this article paved the way for a solid theoretical foundation for compositional verification of parallel and distributed systems.
-
-We are currently extending this work,  looking at further properties of FH-bisimulation, but also
-the relations with existing equivalences on both closed and open systems. In particular, our model being significantly different from those considered in \cite{IngolfsdottirL:2001}, it
-would be interesting to compare our "FH" family of bisimulations with the hierarchy of symbolic bisimulations from these authors.
-We also plan to apply open pNets to the study of complex composition
-operators in a symbolic way, for example in the area of parallel
-skeletons, or distributed algorithms.
-We have developed tool support for computing the
-symbolic semantics in term of open automata \cite{QBMZ-AVOCS18}, and have
-developed algorithms to check strong FH-bisimulation \cite{hou:hal-02406098}.  
-Naturally we are now working toward an implementation of weak FH-Bisimulation. 
-The challenges here, in the context of our symbolic systems, is not so much algorithmic complexity,
-as was the case with classical weak bisimulation on finite models, but decidability and termination.
-Two main directions should be explored, either with an explicit construction of the weak transition, but this step in
-itself may introduce non-termination, or a direct implementation of the weak bisimulation definition, without
-constructing the weak automaton. We can expect that optimisations here in the symbolic setting would be quite different from the classical case.
-
-\bibliographystyle{lncs/splncs}
-
-% \bibliography{oasis,biblio}
-\bibliography{biblio}
-
-\newpage
-\appendix    
-\section{Proof on FH-bisimulation}
-\subsection{Bisimulation is an equivalence: Proof of Theorem~\ref{thm-equiv}}\label{thm-equiv-proof}~\\
-        \emph{Suppose $\mathcal{R}$ 
-       	is an FH-bisimulation. Then $\mathcal{R}$ is an equivalence, that is, 
-       	$\mathcal{R}$ is 
-       	reflexive, symmetric and transitive.
-       	}
-%%% A PROOF WITH CONSTRUCTIVE AERGUMENTS BUT THAT DOES NOT WORK
-
-%       \begin{proof}
-%
-%       It is trivial to check reflexivity and symmetry. Here we focus on the
-%transitivity. 
-%To prove transitivity of strong FH-bisimulation on pNets it is sufficient to prove 
-%transitivity of the strong FH-bisimulation on states of their Open Automata. Consider 3 
-%open automata 
-%$\mathcal{T}_1$, $\mathcal{T}_2$, $\mathcal{T}_3$ and states $s^1$, $s^2$, $s^3$ in 
-%those 
-%automata\footnote{We omit the constraints stating that each $s^i_x$ is in the states of 
-%$\mathcal{T}_i$ for the sake of readability}.
-%Suppose we have $\mathcal{R}$ an FH-bisimulation relation between states of 
-%$\mathcal{T}_1$ and of  $\mathcal{T}_2$; members of $\mathcal{R}$ are of the form 
-%$(s^1,s^2|\Pred)$.
-%Suppose we also  have $\mathcal{R}'$ an FH-bisimulation relation between states of 
-%$\mathcal{T}_2$ and of  $\mathcal{T}_3$; members of $\mathcal{R}2$ are of the form 
-%$(s^2,s^3|\Pred\,')$.
-%We use $\fv$ a function returning the free variables of a term/automaton.
-%
-%Let $\mathcal{R}''$ be the relation (We denote $\Phi$ a set of renamings): 
-%
-%%\begin{mathpar}
-%%\inferrule{}
-%%{}
-%%\end{mathpar}
-%
-%\[\mathcal{R}'' = \Big\{(s^1,s^3|\Pred\,'')\Big|
-%\displaystyle
-% \begin{array}[t]{l}\exists (s^2_p)^{p\in P}.\,\exists (\Phi_p)^{p\in P}.\,\\
-%\quad 
-%	\big(\begin{array}{l}
-%	\forall p\in P.\, (s^1,s^2_p|\Pred)\in\mathcal{R}\land 
-%	(s^2_p,s^3|\Pred\,')\in\mathcal{R}'\land \\
-%	 \forall\ \phi\in\Phi_p.\,
-%	  \fv((\Pred\land\Pred')\phi)\subseteq \fv(\mathcal{T}_1)\cup\fv(\mathcal{T}_3) \land
-%	  \dom(\phi)\subseteq \fv(\mathcal{T}_2)
-%	\end{array}
-%	\big)\\
-%\quad
-%\land ~\Pred'' =\displaystyle\bigvee_{\begin{array}{l}
-%	p\in P\\\phi\in \Phi_p
-%	\end{array}} (\Pred\land\Pred\,')\phi
-%	
-%\end{array}\Big\}
-%\]
-%%(s^1,s^2|\Pred)\in\mathcal{R}\\ (s^2,s^3|\Pred\,')\in\mathcal{R}' 	
-%%}\!\!\!\!\!\exists \phi.\begin{array}[t]{l} \\
-%%\land 
-%%\\
-%%\land 
-%%\\
-%\TODO{s2p is the family of states that relate s1 and s2 big phi is the set of renamings 
-%for each s2 in the family}
-%
-%The relation is built as follows: for each pair of state $s^1$, $s^3$, for each state 
-%$s^2$ such that $\mathcal{R}$ relates $s^1$ and $s^2$, and $\mathcal{R}'$ relates $s^2$ 
-%and $s^3$, we take the conjunction of the two predicates. The predicates for different 
-%values of $s^2$ are collected by a disjunction. 
-%Finally, a set of substitutions should ensure that the 
-%free variables of the predicates are only the ones of $\mathcal{T}_1$ and 
-%$\mathcal{T}_1$. These substitutions somehow express the different ways to match the two 
-%predicates by eliminating the 
-%free variables. We simplify the proof to the case where a single substitution is 
-%necessary for each state $s^2$; the extension to a set of substitution is relatively 
-%simple but complicates the notations. $\phi_p$ is this set of substitutions in the proof 
-%below.
-%
-% We will show
-%that $\mathcal{R}''$ is an FH-bisimulation. Consider 
-%$(s^1,s^3|\Pred\,'')\in\mathcal{R}''$. Then there is a set of states of 
-%$\mathcal{T}_2$ relating $s^1$ and $s^3$, let $(s^2_p)^{p\in P}$ be this family.  
-%For any $p\in P$ by definition of $\mathcal{R}''$,
-%$(s^1,s^2_p|\Pred_p)\in\mathcal{R}$,  and $(s^2_p,s^3|\Pred\,'_p)\in\mathcal{R}$. 
-%Additionally we have $\Pred\,'' = \bigvee_{p\in P} (\Pred_p\land\Pred_p)\,'\phi_p$.
-%We have 
-%the 
-%following by definition of bisimulation.
-%For any open transition $OT$ in $\mathcal{T}_1$ originating from $s^1$:
-%
-%\begin{mathpar}
-%
-%\inferrule*[myfraction=\reddottedrule]
-%{\{s^1_i\xrightarrow{a_i}_i {s^{1}}'_i\}^{i\in I_1}, % , s^1_i,s^{1'}_i\in
-%	%States(I_1)
-%	\{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
-%{s^1 \xrightarrow {v} {s^{1}}'}
-%
-%\end{mathpar}
-%
-%there exist open transitions $OT_{p x}^{x\in X} \subseteq \mathcal{T}_2$:
-%
-%\begin{mathpar}
-%
-%%    \left( fresh \ \set{a_i}, \set{b_j}, v_x.\ \
-%\inferrule*[myfraction=\reddottedrule]
-%{\{s^{2}_{pi}\xrightarrow{a_{p i x}}_i s^{2}_{p i x}\}^{i\in I_{2 p x}},
-%	\{\xrightarrow{b_{j p x}}_j\}^{j\in J_{2px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
-%{s^2_p \xrightarrow {v_{px}} s^{2}_{px}}
-%%         \right)
-%\end{mathpar}
-%
-%such that  $\forall x, J_1=J_{2px}, (s^{1'},s^{2}_{px}|\Pred_{target_{px}})\in 
-%\mathcal{R}$;
-%and  \\
-%
-%$\Pred_p \land \Pred_{OT}\\
-%\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-%\left( \forall j. b_j=b_{jpx}  \Rightarrow \Pred_{OT_{px}}
-%\land v\!=\!v_{px} \land
-%\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)$
-%
-%for any open transition $OT_{px}$, since
-%$(s^2_p,s^3|\Pred\,^\prime_p)\in\mathcal{R}'$ there exist open transitions
-%$OT_{pxy}^{x\in X, y\in Y} \subseteq \mathcal{T}_3$: 
-%
-%\begin{mathpar}
-%
-%%    \left( fresh \ \set{a_i}, \set{b_j}, v_x.\ \
-%\inferrule*[myfraction=\reddottedrule]
-%{\{s^{3}_i\xrightarrow{a_{i p x y}}_i s^{3}_{i p x y}\}^{i\in I_{3 p x y}},
-%	\{\xrightarrow{b_{j p x y}}_j\}^{j\in J_{3pxy}}, \Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
-%{s^3 \xrightarrow {v_{pxy}} s^{3}_{pxy}}
-%%         \right)
-%
-%\end{mathpar}
-%such that  $\forall y, J_{2px}=J_{3pxy}, 
-%(s^{2}_x,s^{3}_{pxy}|\Pred_{target_{pxy}})\in \mathcal{R}'$; and  \\
-%$\Pred\,'_p \land \Pred_{OT_{px}}\\
-%\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
-%\left( \forall j. b_{jpx}=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
-%\land v_{px}\!=\!v_{pxy} \land
-%\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.
-%
-%This is verified for each $p\in P$. Overall,  we have a family of open transitions 
-%$OT_{pxy}^{p\in 
-%P, x\in X, 
-%y\in Y} \subseteq \mathcal{T}_3$ that should simulate \emph{OT}.
-%
-%First, $\forall y, \forall x, \forall p, J_1=J_{2px}=J_{3pxy}, 
-%({s^{1}}',s^{3}_{pxy}|\Pred\,'_{target_{pxy}})\in \mathcal{R}''$. 
-%Indeed for any 
-%$p$, 
-%$x$, and 
-%$y$, $s^2_{px}$
-%relate ${s^{1}}'$ and $s^{3}_{pxy}$, indeed
-%$(s^{1'},s^{2}_{px}|\Pred_{target_{px}})\in \mathcal{R}$
-% and $(s^{2}_x,s^{3}_{pxy}|\Pred_{target_{pxy}})\in \mathcal{R}'$. 
-% More precisely, $s^{2}_{px} \in ({s^{2}_p}')^{p\in P'}$ where $({s^{2}_p}')^{p\in 
-% P'}$ 
-% is 
-% the set of states relating ${s^{1}}'$ and $s^{3}_{pxy}$.
-%Consequently, for all $p$, $x$, $y$,\\
-% $\left(\exists \phi'.\,(\Pred_{target_{px}}\land 
-%\Pred_{target_{pxy}})\phi'\land \fv((\Pred\land\Pred)\phi')\subseteq 
-%\fv(\mathcal{T}_1)\cup\fv(\mathcal{T}_3)\right)\implies 
-%\Pred\,'_{target_{pxy}}$ \\
-%This is one element of the  disjunction defining the 
-%predicate 
-%relating ${s^{1}}'$ and $s^{3}_{pxy}$ in the definition of $\mathcal{R}''$.
-%
-%Second, we need \\
-%\begin{small}
-%$\Pred\,'' \land \Pred_{OT}\\
-%\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
-%\left( \forall j. b_j=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
-%\land v\!=\!v_{pxy} \land
-%\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
-%\end{small}
-%
-%We have, for all $p$
-%\begin{small}
-%$\Pred_p \land \Pred_{OT}\land\Pred'_p\\
-%\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-%\left( \forall j. b_j=b_{jpx}  \Rightarrow \Pred_{OT_{px}}
-%\land v\!=\!v_{px} \land
-%\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\land\Pred'_p\\
-%%
-%\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-%\left( \forall j. b_j=b_{jpx}  \Rightarrow (\Pred_{OT_{px}}\land\Pred'_p)
-%\land v\!=\!v_{px} \land
-%\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\\
-%%
-%\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-%\big( \forall j. b_j=b_{jpx}  \Rightarrow (\bigvee_{y\in Y} 
-%\big( \forall j'. b_{j'px}=b_{j'pxy}  \Rightarrow \Pred_{OT_{pxy}}
-%\land v_{px}\!=\!v_{pxy}\\\hspace{3em}~ \land
-%\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\big))
-%\land v\!=\!v_{px} \land
-%\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\\
-%%
-%\hspace{1cm} \implies\!\!\! \bigvee_{x\in X} \bigvee_{y\in Y}
-%\big( \forall j, j'. b_j=b_{jpx} \land b_{j'px}=b_{j'pxy}
-%\Rightarrow \big( 
-%\Pred_{OT_{pxy}}
-%\land v\!=v_{px}\!=\!v_{pxy}\\\hspace{3em}~ \land
-%\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}
-% \land
-%\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\big)
-%$
-%
-%\end{small}
-%
-%Additionally, the Post substitutions only have an effect on the  predicates that  use 
-%some of the 
-%substituted 
-%variables, and because of the domain of the substitutions we have:\\
-%$(\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\land 
-%\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}})\phi\\
-%%
-%= 
-%(\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land
-%\Pred_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}) 
-%\phi\\
-%%
-%= 
-%((\Pred_{target_{px}}\land
-%\Pred_{target_{pxy}})\subst{\Post_{OT_{px}}}\phi) 
-%\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\\
-%%
-%\implies\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}
-%\subst{\Post_{OT_{pxy}}}\\
-% $
-%Finally, gathering the previous results, and using the fact that only variables of 
-%$\mathcal{T}_2$ are changed by $\phi$ substitutions:
-%
-%$\Pred\,'' \land \Pred_{OT}\\
-%\hspace{1cm} \implies\!\!\! \bigvee_{p\in P}(\Pred_p \land 
-%\Pred_{OT}\land\Pred\,'_p)\phi\\
-%\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
-%\left( \forall j. b_j=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
-%\land v\!=\!v_{pxy} \land
-%\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)
-%$
-%
-%This is the expected property.
-%
-%
-%\smallskip
-%Concerning the other direction of bisimulation, it is sufficient to notice that the role 
-%of $s^1$ and $s^3$ in the definition of $\mathcal{R}''$ is symmetrical, and thus the 
-%proof is similar.
-%
-%       \end{proof}
-%       
-%       \bigskip
-%       
-%       
-              \begin{proof}
-
-       	It is trivial to check reflexivity and symmetry. Here we focus on the
-       	transitivity. 
-       	To prove transitivity of strong FH-bisimulation on pNets it is sufficient to 
-       	prove 
-       	transitivity of the strong FH-bisimulation on states. Consider 3 open automata 
-       	$\mathcal{T}_1$, $\mathcal{T}_2$, $\mathcal{T}_3$ and states $s$, $t$, $u$ 
-       	in those 
-       	automata\footnote{We omit the constraints stating that each $s_x,\,t_x,\,u_x$ is 
-       	in the 
-       	states of 
-       		$\mathcal{T}_1,\,\mathcal{T}_2,\,\mathcal{T}_3$ for the sake of readability}.
-       	Suppose we have $\mathcal{R}$ an FH-bisimulation relation between states of 
-       	$\mathcal{T}_1$ and of  $\mathcal{T}_2$; members of $\mathcal{R}$ are of the form 
-       	$(s,t|\Pred_{s,t})$.
-       	Suppose we also  have $\mathcal{R}'$ an FH-bisimulation relation between states 
-       	of 
-       	$\mathcal{T}_2$ and of  $\mathcal{T}_3$; members of $\mathcal{R}'$ are of the 
-       	form 
-       	$(t,u|\Pred_{t,u})$.
-
-       	Let $\mathcal{R}''$ be the relation: 
-       	\[\mathcal{R}'' = 
-       	\{(s,u|\Pred_{s,u})\,\,\Big|\,\Pred_{s,u}=\hspace{-0.7cm}\bigvee_{\begin{array}{c}       		
-       		(s,t|\Pred_{s,t})\in\mathcal{R}\\ (t,u|\Pred_{t,u})\in\mathcal{R}' 	
-       		\end{array}
-       }\hspace{-0.5cm}\Pred_{s,t}\land\Pred_{t,u}\}\]
-
-This relation is the adaptation of the transitivity to the conditional relationship that 
-defines a bisimulation. Indeed the global disjunction together with the conjunction of 
-predicates plays exactly the role of the intermediate element in a transitivity rule: 
-``there exists an intermediate state'' corresponds to the global disjunction, and the 
-conjunction of states expresses the intermediate predicate is used to ensure 
-satisfiability of the predicate relating the first state to the last one.
-
-       	The relation is built as follows: for each pair of states $s$, $u$, for each 
-       	state 
-       	$t$ such that $\mathcal{R}$ relates $s$ and $t$, and $\mathcal{R}'$ relates 
-       	$t$ 
-       	and $u$, we take the conjunction of the two predicates. The predicates for 
-       	different 
-       	values of $t$ are collected by a disjunction.
-
-       	We will show
-       	that $\mathcal{R}''$ is an FH-bisimulation. Consider 
-       	$(s,u|\Pred_{s,u})\in\mathcal{R}''$. Then there is a set of states of 
-       	$\mathcal{T}_2$ relating $s$ and $u$, let $(t_p)^{p\in P}$ be this family.  
-       	       	We have $\Pred_{s,u} = \displaystyle{\bigvee_{p\in P} \Pred_{s,p}\land\Pred_{p,u}}$.
-
-\medskip
-
-       	For any $p\in P$ by definition of $\mathcal{R}''$,
-       	$(s,t_p|\Pred_{s,p})\in\mathcal{R}$,  and 
-       	$(t_p,u|\Pred\,'_{p,u})\in\mathcal{R}'$. 
-       	We have 
-       	the 
-       	following by definition of bisimulation:
-       	For any open transition $OT$ in $\mathcal{T}_1$ originating from $s$.
-       	\begin{mathpar}
-       	\openrule
-       	{
-       		\beta_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
-       	{s \OTarrow {\alpha} {s}'}     	
-       	\end{mathpar}
-
-       	There exist open transitions $OT_{p x}^{x\in X} \subseteq \mathcal{T}_2$:
-
-       	\begin{mathpar} 
-       	%    \left( fresh \ \set{a_i}, \set{b_j}, v_x.\ \
-       	\openrule
-       	{
-       		\beta_{j p x}^{j\in J_{px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
-       	{t_p \OTarrow {\alpha_{px}} t_{p x}}\qquad (*)
-       	%         \right)
-       	\end{mathpar}
-
-       	such that  $\forall x, J_1=J_{px}, (s',t_{px}|\Pred_{{px}})\in 
-       	\mathcal{R}$;
-       	and  \\
-
-       	$\Pred_{s,p} \land \Pred_{OT}\\
-       	\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}
-       	\left( \forall j. \beta_j=\beta_{jpx}  \land \Pred_{OT_{px}}
-       	\land \alpha\!=\!\alpha_{px} \land
-       	\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\right)}$\\
-
-For any open transition $OT_{px}$, since
-       	$(t_p,u|\Pred_{p,u})\in\mathcal{R}'$ there exist open transitions
-       	$OT_{pxy}^{y\in Y} \subseteq \mathcal{T}_3$:
-
-       	\begin{mathpar}  	
-       	%    \left( fresh \ \set{a_i}, \set{b_j}, v_x.\ \
-       	\openrule
-       	{
-       		\beta_{j p x y}^{j\in J_{pxy}}, 
-       		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
-       	{u \OTarrow {\alpha_{pxy}} u_{pxy}}\qquad (**)
-       	%         \right)    	
-       	\end{mathpar}
-       	such that  $\forall y, J_{px}=J_{pxy}, 
-       	(t_{px},u_{pxy}|\Pred_{{pxy}})\in \mathcal{R}'$; and  \\
-       	$\Pred\,'_{p,u} \land \Pred_{OT_{p x}}\\
-       	\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}\!
-       	\left( \forall j.\beta_{jpx}\!=\!\beta_{jpxy} \land\! \Pred_{OT_{pxy}}\!
-       	\land\! \alpha_{px}\!=\!\alpha_{pxy} \!\land\!
-       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}\!\uplus\!\Post_{OT_{pxy}}}\right)}$\\
-
-       	This is verified for each $p\in P$.\\ Overall,  we have a family of open 
-       	transitions 
-       	$OT_{pxy}^{p\in 
-       		P, x\in X, 
-       		y\in Y} \subseteq \mathcal{T}_3$ that should simulate $OT$.
-
-       	First, we have $\forall y, \forall x, \forall p,  J_1=J_{px}=J_{pxy}, 
-       	({s}',u_{pxy}|\Pred\,'_{{pxy}})\in \mathcal{R}''$ for some $\Pred\,'_{{pxy}}$. 
-       	Indeed for any 
-       	$p$, 
-       	$x$, and 
-       	$y$, $t_{px}$
-       	relates ${s}'$ and $u_{pxy}$, we have
-       	$(s',t_{px}|\Pred_{{px}})\in \mathcal{R}$
-       	and $(t_{px},u_{pxy}|\Pred_{{pxy}})\in \mathcal{R}'$. 
-       	More precisely,  $t_{px} \in ({t'_p})^{p\in P'}$ where $({t'_p})^{p\in 
-       		P'}$ and $P'\subseteq P$  is 
-       	the set of states relating ${s}'$ and $u_{pxy}$ (the states used in the open transition must belong to the set of states ensuring the transitive relation).
-       	Additionally, for all $p$, $x$, $y$, $\Pred_{px}\land 
-       	\Pred_{{pxy}}\implies 
-       	\Pred\,'_{{pxy}}$ (this is one element of the  disjunction defining the 
-       	predicate $\Pred\,'_{{pxy}}$
-       	relating ${s}'$ and $u_{pxy}$ in the definition of $\mathcal{R}''$).
-
-One can notice that, as bisimulation predicates are used to relate states that 
-belong to two different open automata, the free variables of these predicates 
-that do not belong to the two related automata can safely be renamed to avoid any 
-name clash. In practice,
-we can suppose that $\Pred\,'_{{pxy}}$ does not 
-contain the variables of $\mathcal{T}_2$ because it is used to relate states of $\mathcal{T}_1$ and $\mathcal{T}_3$ .
-Indeed if $\Pred\,'_{{pxy}}$ uses variables of 	$\mathcal{T}_2$, we can consider instead another predicate that is equivalent to $\Pred\,'_{{pxy}}$ and does not
-contain the variables of 	$\mathcal{T}_2$ (this is safe according to the semantic interpretation of open automata and relations). 
-Similarly, we can suppose that $\Pred_{{px}}$ contains no 
-variable in $\mathcal{T}_3$, and $\Pred_{{pxy}}$ contains no 
-variable in $\mathcal{T}_1$.
-
-       	Second, by definition of bisimulation we need (recall that $\Pred_{s,u}$ is the 
-       	original predicate relating $s$ and $u$ by definition of the transitive 
-       	closure):\\
-       	\begin{small}
-       		$\Pred_{s,u} \land \Pred_{OT}\\
-       		\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
-       		\left( \forall j. \beta_j=\beta_{jpxy}  \land \Pred_{OT_{pxy}}
-       		\land \alpha\!=\!\alpha_{pxy} \land
-       		\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{pxy}}}\right)}$.
-       	\end{small}
-
-From (*) and (**) we have, for all $p$
-       	\begin{small}
-       		$\Pred_{s,p} \land \Pred_{OT}\land\Pred_{p,u}\\
-       		\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}
-       		\left( \forall j. \beta_j=\beta_{jpx}  \land \Pred_{OT_{px}}
-       		\land \alpha\!=\!\alpha_{px} \land
-       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\right)\land\Pred_{p,u}}\\
-       		%
-       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-       		\left( \forall j. \beta_j=\beta_{jpx}  \land 
-       		(\Pred_{OT_{px}}\land\Pred_{p,u})
-       		\land \alpha\!=\!\alpha_{px} \land
-       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\right)\\
-       		%
-       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-       		\big( \forall j. \beta_j=\beta_{jpx}  \land (\bigvee_{y\in Y} 
-       		\big( \forall j'. \beta_{j'px}=\beta_{j'pxy}  \land \Pred_{OT_{pxy}}
-       		\land \alpha_{px}\!=\!\alpha_{pxy}\\~\hspace*{2em}~ \land
-       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}\big))
-       		\land \alpha\!=\!\alpha_{px} \land
-       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\big)\\
-       		%
-       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X} \bigvee_{y\in Y}
-       		\big( \forall j, j'. \beta_j=\beta_{jpx} \land \beta_{j'px}=\beta_{j'pxy}
-       		\land \big( 
-       		\Pred_{OT_{pxy}}
-       		\land \alpha\!=\alpha_{px}\!=\!\alpha_{pxy}\\~\hspace*{2em}~ \land
-       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}
-       		\land
-       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\big)\big)
-       		$
-
-       	\end{small}
-
-By construction, four substitutions $\subst{~}$ only have an effect on the  
-variables of the open automaton they belong to, they also produce terms containing only 
-variables of the open automaton they belong to. Finally, because of the domain of the 
-substitutions of the predicates, we have:\\
-       	$\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\land 
-       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}\uplus
-       	\Post_{OT_{pxy}}}\Leftrightarrow\\ % we changed =
-       	\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}\land
-       	\Pred_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}\\
-       	\implies\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus
-       	\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}
-       	\Leftrightarrow\\ % we changed = 
-       	 \Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{pxy}}} $\\
-
-       	This allows us to conclude, with $\Pred_{s,u} = \bigvee_{p\in P} 
-       	\Pred_{s,p}\land\Pred_{p,u}$:
-
-      	\begin{small}     	
-$\displaystyle{\Pred_{s,u} \land \Pred_{OT}}\\
- \implies\!\!\! \bigvee_{p\in P} (
-	\Pred_{s,p}\land\Pred_{p,u} \land \Pred_{OT})\\
-\hspace{1cm} \implies\!\!\!\bigvee_{p\in P}
- \bigvee_{x\in X} \bigvee_{y\in Y}
-\big( \forall j, j'.\beta_j=\beta_{jpx} \land \beta_{j'px}=\beta_{j'pxy}
-\land \Pred_{OT_{pxy}}\\
-~\hspace*{2em}~\land \alpha\!=\!\alpha_{px}\!=\!\alpha_{pxy}\land\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus \Post_{OT_{pxy}}}\big)
-\\
-\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
-\left( \forall j. \beta_j\!=\!\beta_{jpxy}  \land \Pred_{OT_{pxy}}
-\land \alpha\!=\!\alpha_{pxy} \land
-\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{pxy}}}\right)$
-  \end{small}
-
-       	\smallskip
-       	Concerning the other direction of bisimulation, it is sufficient to notice that 
-       	the role 
-       	of $s$ and $u$ in the definition of $\mathcal{R}''$ is symmetrical, and thus 
-       	the 
-       	proof is similar.
-
-       \end{proof}
-
-\subsection{Composition Lemmas}       
-       The proofs of the composition theorems for FH-bisimulation rely on two main lemmas,
-dealing respectively with the decomposition of a composed behaviour
-between the context and the internal pNet, and with their recomposition.
-
-\subsubsection*{{\bf Lemma~\ref{lem-decompose}}: Open transition decomposition} ~\\
- Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$}.
-	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose:
-	\[ P[Q]_{j_0}  
-		\models
-		{\openrule
-			{
-				\beta_j^{j\in J}, \Pred,  
-				\Post}
-			{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
-				\ostate{s_i'^{\, i\in L}}}
-		}
-	\]
-		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.
-		 Then, there exist $\alpha_Q$, $\Pred\,'$, $\Pred\,''$, 
-		$\Post\,'$, $\Post\,''$ s.t.:\\[-2ex]
-		%\[
-		\begin{mathpar}
-		P\models{\openrule
-			{
-				\beta_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
-				\Pred\,',  
-				\Post\,'}
-			{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {\alpha}
-				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
-		}%\]
-	\vspace{-2.2ex}\\\text{and~~}
-		%\[
-		Q\models{\openrule
-			{
-				\beta_j^{j\in J\cap\Holes(Q)}, \Pred\,'',  
-				\Post\,''}
-			{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
-				\ostate{s_i'^{\,i\in L_Q}}}
-		}%\]
-		\end{mathpar}
-		and  $\Pred \iff \Pred\,'
-		\land \Pred\,''\land \alpha_Q=\beta_{j_0}$, $\Post=\Post\,'\uplus 
-		\Post\,''$ where $\Post\,''$ is the restriction of $\Post$ over variables  
-		$\vars(Q)$.
-
-\textbf{Preliminary note:}
-The introduction of fresh variables introduce alpha-conversion at many points 
-of the proof; we 
-	only 
-	give major arguments concerning alpha-conversion to make the proof readable; in 
-	general, fresh variables appear in each transition inside
-        terms $\beta_j$, $v$, and 
-	$\Pred$.
-
-   \begin{proof}
-
-Consider rule \TrDeux\ in 
-       Definition~\ref{def:operationalSemantics}, applied to the pNet $P[Q]_{j_0}$. 	
-	\noindent
-\begin{small}	
-\begin{mathpar}
-    \mprset {vskip=.8ex}
-\inferrule
-    {
-\Leaves(\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in 
-    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
-k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
-\\
-\\     	
-	\forall m\!\in\! I_1. {\pNet_m 
-	\models\openrule
-    	{
-    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
-    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
-    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
-  \qquad
-\forall m\!\in\! I_2.		{ \pNet_m 
-    	 \models
-    	\openrule
-    	{\emptyset, \Pred_m, \Post_m}
-    	{\ostate{s_m} \OTarrow {\alpha_m}
-    		\ostate{s_m'}} }\\\\
-     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
-    	\Pred = \bigwedge_{m\in I_1\uplus I_2}\!\! \Pred_m \land
-    	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2},\beta_j^{j\in J},\alpha)\\ 
-    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
-    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
-    }
-    {\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
-    	\models
-    	{\openrule
-    		{
-    		{\beta_j}^{j\in J^\prime}, \Pred,  \biguplus_{m\in I_1\uplus I_2} 
-    		\Post_m}
-    		{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
-    			\ostate{(s_i^\prime)^{i\in L}}}
-    	}
-    }\quad\TrDeux
-\end{mathpar}
-
-\end{small}
-%\begin{mathpar}
-%    \mprset {vskip=1ex}
-%\inferrule
-%    {
-%\Leaves(\mylangle \set{\pNet}, \set{\Sort}, \symb{SV}_k^{k\in 
-%    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
-%k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
-%\\
-%\\     	
-%	\forall m\!\!\in\!\! I_1. {\pNet_m 
-%	\models\openrule
-%    	{
-%    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
-%    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
-%    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
-%  \qquad
-%\forall m\!\!\in\!\! I_2.		{ \pNet_m 
-%    	 \models
-%    	\openrule
-%    	{\emptyset, \Pred_m, \Post_m}
-%    	{\ostate{s_m} \OTarrow {\alpha_m}
-%    		\ostate{s_m'}} }\\\\
-%     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
-%    	\Pred = \bigwedge_{m\in (I_1\uplus I_2)}\!\! \Pred_m \land
-%    	\Predsv(SV_k,\alpha_m^{m\in (I_1\uplus I_2)},\beta_j^{j\in J},\alpha)\\ 
-%    		I' = \biguplus_{m\in I_1}\!\! I_m \uplus I_2
-%    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
-%    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
-%    }
-%    {\mylangle \set{\pNet}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
-%    	\models
-%    	{\openrule
-%    		{
-%    		{\beta_j}^{j\in J^\prime}, \Pred, \uplus_{m\in I_1\uplus I_2} 
-%    		\Post_m}
-%    		{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
-%    			\ostate{(s_i^\prime)^{i\in L}}}
-%    	}
-%    }
-%\end{mathpar}
-
-We know each premise is \True\ for $P[Q]_{j_0}$. 
-  $j_0\in I_1$ because $Q$ is not a pLTS. We try to prove the equivalent premise for 
-$P$.
-
-First, $K$ and the synchronisation vector $SV_k$ are unchanged (however 
-$j_0$ passes from 
-the set of sub-pNets to the set of holes). 
-%Then $SV=clone(\alpha_j^{j\in I_k\uplus\{j_0\}\uplus J_k})$.
-We have $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$.
-
-Now focus on the OTs of the sub-pNets. For each $m\in I_1\uplus I_2$ we have one of the two 
-following OT:\\
-either $m$ in $I_1$
-\[
-\pNet_m \models\openrule
-    	{
-    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
-    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
-    		\ostate{(s_i^\prime)^{i\in L_m}}}\]
-or, $m$ in $I_2$
-\[{ \pNet_m 
-    	 \models
-    	\openrule
-    	{\emptyset, \Pred_m, \Post_m}
-    	{\ostate{s_m} \OTarrow {\alpha_m}
-    		\ostate{s_m'}}}\]
-
-Only elements of $(I_1\uplus I_2)\backslash\{j_0\}$   are useful to assert the premise for reduction of $P$; the last 
-one ensures the open transition for the pNet $Q$ (note that $Q$ is at place $j_0$, and by 
-definition of the open transition 
-for $P[Q]_{j_0}$, 
-$L_{j_0}=L_Q$, and $J_{j_0}=	J\cap\Holes(Q)$):\\[-2ex]
-	\[Q\models{\openrule
-		{
-			\beta_j^{j\in J\cap\Holes(Q)}, \Pred_{j_0},  
-			\Post\,''}
-		{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_{j_0}}
-			\ostate{(s_i')^{\, i\in L_Q}}}
-	}\]
-
-This already ensures the second part of the conclusion of the lemma, i.e. the OT for $Q$ 
-if we 
-choose  $\alpha_Q=\alpha_{j_0}$ and $\Pred\,''= \Pred_{j_0}$. 
-Considering 
-the OT of $P$ we have another  $J'$ that is $J'_p=J'\setminus\Holes(Q)\uplus 
-\{j_0\}$; we denote $I'_1=I_1\setminus \{j_0\}$ the predicate is 
-$\displaystyle{\Pred\,'=\!\!\!\!\!\bigwedge_{m\in I_1'\uplus I_2}\!\!\!\!\!\Pred_m  \land \Predsv(SV_k,\alpha_m^{m \in I'_1\uplus I_2},\beta_j^{j\in J\cup \{j_0\}},\alpha)}$\\
-where
-\begin{multline*}
-\Predsv(SV_k,\alpha_m^{m \in I'_1\uplus I_2},\beta_j^{j\in 
-J\cup 
-\{j_0\}},\alpha)\Leftrightarrow \\
-\forall i\in I'_1\uplus I_2.\, \alpha_i=\alpha'_i\land \forall j \in J\cup \{j_0\}.\, 
-\beta_j=\alpha'_j 
-\land 
-\alpha=\alpha'
-\land e_b
-\end{multline*}
-
- Modulo renaming of fresh variables, this is identical to the predicate that 
-occurs in 
-the source open transition except $\alpha_{j_0}=\alpha'_{j_0}$ has been replaced by  
-$\beta_{j_0}=\alpha'_{j_0}$. As $\alpha_{j_0}=\alpha_Q$ and $\beta_{j_0}$ is free, we 
-have $\beta_{j_0}=\alpha'_{j_0}\land \beta_{j_0}=\alpha_Q \iff 
-\alpha_{j_0}=\alpha'_{j_0}$.
-Thus, $\Pred \iff (\Pred\,'
-		\land \Pred\,'')\land \alpha_Q=\beta_{j_0}$. 
-Finally, Post 
-%conditions are easily split\footnote{\TODO{moved. could
-%    even remove...?}Note that if the rules are not simplified, no
-%  post-condition range over the variables of $P$ and $Q$ at the same
-%  time} 
-into conditions of the context $P$ and the pNet $Q$ (they are
-builts similarly as they only deal with  
-leaves): $\Post=\Post\,'\uplus \Post\,''$. This concludes the 
-proof as we checked all the premises of the open transition for both $P$ and $Q$. We obtain the following reduction by the rule \TrDeux:
-	\noindent
-	\begin{small}
-\begin{mathpar}
-    \mprset {vskip=.8ex}
-\inferrule
-    {
-\Leaves(\mylangle {\pNet}_m^{m\in I\setminus\{j_0\}}, \set{\Sort}, \symb{SV}_k^{k\in 
-    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
-k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
-\\
-\\     	
-	\forall m\!\!\in\!\! I_1\setminus\{j_0\}. {\pNet_m 
-	\models\openrule
-    	{
-    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
-    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
-    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
-  \qquad
-\forall m\!\!\in\!\! I_2.		{ \pNet_m 
-    	 \models
-    	\openrule
-    	{\emptyset, \Pred_m, \Post_m}
-    	{\ostate{s_m} \OTarrow {\alpha_m}
-    		\ostate{s_m'}} }\\\\
-     J' = \biguplus_{m\in I_1 \setminus \{j_0\}}\!\! J_m \uplus J 	\\
-    	\Pred\,' = \bigwedge_{m\in I_1\uplus I_2\setminus\{j_0\}}\!\! \Pred_m \land
-    	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2 \setminus \{j_0\}},\beta_j^{j\in J\cup\{j_0\}},\alpha)\\ 
-    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1\setminus\{j_0\}}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
-    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
-    }
-    {\mylangle {\pNet}_m^{m\in I\setminus\{j_0\}}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
-    	\models
-    	{\openrule
-    		{
-    		{\beta_j}^{j\in J\setminus \Holes(Q)\uplus \{j_0\}}, \Pred\,',  \biguplus_{m\in I_1\setminus\{j_0\}\uplus I_2} 
-    		\Post_m}
-    		{\ostate{s_i^{i\in L\setminus L_Q}} \OTarrow {\alpha}
-    			\ostate{(s_i^\prime)^{i\in L\setminus L_Q}}}
-    	}
-    }
-\end{mathpar}
- \end{small}
-\end{proof}
-
-In general, the actions that can be emitted by $Q$ is  a subset of the possible 
-actions of the holes, and the predicate involving $v_Q$ and the synchronisation vector is 
- more restrictive than the one involving only the variable $\beta_{j_0}$. This has no 
- impact 
- on the previous proof and this restriction  results from the composition of predicates.
-%\TODO{is this useful? = yes, I think }
-
-\subsubsection*{ \bf{Lemma~\ref{lem-compose}}:  Open transition composition}~\\
-	Consider two pNets $P$ and $Q$ where $P$ is not a pLTS. Suppose $j_0\in J$ and:\\[-1ex]
-\begin{mathpar}
-%\[
-P\models{\openrule
-	{
-		\beta_j^{j\in J}, 
-		\Pred,  
-		\Post}
-	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
-		\ostate{s_i'^{\, i\in L}}}
-}%\]
-\text{~~\qquad\qquad~and~\qquad\qquad~~}
-%\[
-Q\models{\openrule
-	{
-		\beta_j^{j\in J_Q},
-		 \Pred\,',  
-		\Post\,'}
-	{\ostate{s_i^{i\in L_Q}} \OTarrow {\alpha_Q}
-		\ostate{s_i'^{\, i\in L_Q}}}
-}%\]
-\end{mathpar}
-Then, we have:\\[-2ex]
-	\[ P[Q]_{j_0}  
-	\models
-	{\openrule
-		{
-			\beta_j^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
-			\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0},  
-			\Post\uplus \Post\,'}
-		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {\alpha}
-			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
-	}
-	\]
-
-Note that this does not mean that any two pNets can be composed and produce an open 
-transition. Indeed, the predicate $\Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0}$ will not 
-be satisfiable if the action of $\alpha_Q$ cannot be matched with $\beta_{j_0}$.
-Note also that $\beta_{j_0}$ is now only used as an intermediate term inside formulas: it 
-does not appear neither as global action nor as an action of a hole.
-
-\begin{proof} 
-Let $P=\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle$.
-Consider first the open transition derived from $P$.
-       Consider each premise of the open transition (constructed by \TrDeux\ in 
-Definition~\ref{def:operationalSemantics}). 
-	\begin{small}
-\begin{mathpar}
-    \mprset {vskip=.8ex}
-\inferrule
-    {
-\Leaves(\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in 
-    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
-k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
-\\
-\\     	
-	\forall m\!\in\! I_1. {\pNet_m 
-	\models\openrule
-    	{
-    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
-    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
-    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
-  \qquad
-\forall m\!\in\! I_2.		{ \pNet_m 
-    	 \models
-    	\openrule
-    	{\emptyset, \Pred_m, \Post_m}
-    	{\ostate{s_m} \OTarrow {\alpha_m}
-    		\ostate{s_m'}} }\\\\
-     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J 	\\
-    	\Pred = \bigwedge_{m\in I_1\uplus I_2}\!\! \Pred_m \land
-    	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2},\beta_j^{j\in J},\alpha)\\ 
-    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
-    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
-    }
-    {\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
-    	\models
-    	{\openrule
-    		{
-    		{\beta_j}^{j\in J^\prime}, \Pred,  \biguplus_{m\in I_1\uplus I_2} 
-    		\Post_m}
-    		{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
-    			\ostate{(s_i^\prime)^{i\in L}}}
-    	}
-    }\quad \TrDeux
-\end{mathpar}  
-\end{small}
-We know each premise is \True\ for $P$ and try to prove the equivalent premise for 
-$P[Q]_{j_0}$ (using the open transition of $Q$). $P[Q]_{j_0}$ exhibits a similar \TrDeux~rule where
-$K$ and the synchronisation vector are unchanged ($j_0$ is now in the set of sub-pNets); 
-$SV_k=\SV{(\alpha'_j)^{j\in I\uplus\{j_0\}\uplus 
-	J}}{\alpha'}{e_b}$. $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$. $I$ and $J$ 
-	are the 
-    set of leaves and holes of $P$, $I_1\uplus I_2$ and $J'$ are the sets of moving 
-    leaves and holes 
-    in the reduction of $P$. All sub-pNets of 
-    must
-    be 
-reduced, we need:%\footnote{again we skip arguments related to renaming of fresh 
-%variables}:
-\[
-    	\forall m\!\in\! I_1\uplus\{j_0\}. {\pNet_m 
-    	\models\openrule
-    	{
-    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
-    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
-    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
-  \]\[
-\forall m\!\in\! I_2.		{ \pNet_m 
-    	 \models
-    	\openrule
-    	{\emptyset, \Pred_m, \Post_m}
-    	{\ostate{s_m} \OTarrow {\alpha_m}
-    		\ostate{s_m'}} }\]
-%\forall m\!\!\in\!\! I\cup \{j_0\}. 	
-%    {\left(\begin{array}{l}
-%	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
-%    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m},
-%    	\{\xrightarrow{\beta_{j}}_j\}^{j\in J_m}, \Pred_m, \Post_m}
-%    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
-%    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
-%		{ \pNet_m 
-%    	 \models
-%    	\inferrule*[myfraction=\reddottedrule]
-%    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
-%    	{\ostate{s_m} \OTarrow {v_m}
-%    		\ostate{s_m'}} \land I_m=\{m\} \land J_m=\emptyset}
-%\end{array}\right)}\]
-the sub-pNet at position $j_0$ is the one filled by $Q$ (we define $P_{j_0}=Q$ and similarly $J_m=J_Q$, $\Pred_m=\Pred\,'$, $\Post_m=\Post\,'$,\ldots are the elements of the OT of Q) which offers an open transition
-by hypothesis, the other open transitions are immediate consequence of the open 
-transition that can be performed by $P$ (premises of \TrDeux).
-The set of moving leaves is the union of the moving leaves in the open transition for $P$ 
-and the ones for $Q$; similarly the moving holes are the union of the moving 
-holes, minus $j_0$: $J'_{PQ}=  J\setminus\{j_0\}\uplus J_Q$. The 
-predicate for the open 
-transition is:\\
- $\displaystyle{\Pred\,''=\!\!\!\!\bigwedge_{m\in I _1\uplus I_2}\!\!\!\Pred_m \land \Pred\,'
-\land \Pred(SV_k,v_i^{i\in I_1\uplus I_2}\uplus(j_0\mapsto v_Q),\beta_j^{j\in 
-J},\alpha)}$. \\
-By definition we have:\\
-$\Pred(SV_k,\alpha_i^{i\in I}\uplus(j_0\mapsto \alpha_Q),\beta_j^{j\in 
-J},v)\Leftrightarrow
-	\forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, \beta_j=\alpha'_j \land 
-	\alpha=\alpha'\land \alpha_Q=\alpha_{j_0}\land e_b$,
-this is equivalent to $\forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, 
-\beta_j=\alpha'_j \land 
-	\alpha=\alpha'\land \alpha_Q=\beta_{j_0}\land \beta_{j_0}=\alpha_{j_0}\land e_b$
- and by definition of $\Pred$ (as obtained by \TrDeux),
-	$\Pred\,''\iff \Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0}$. The post-condition 
-	gathers the post-conditions related to all 
-	the leaves: $\displaystyle{\biguplus_{m\in I_1\cup\{j_0\}\uplus I_2} 
-    		\!\!\!\!\!\Post_m = 	\Post\uplus \Post\,'}$.\\ Finally, the composed open transition can be
-        built by \TrDeux\ as follows
-	\noindent
-	\begin{small}
-\begin{mathpar}
-    \mprset {vskip=.8ex}
-\inferrule
-    {
-\Leaves(\mylangle {\pNet}_m^{m\in I\cup\{j_0\}}, \set{\Sort}, \symb{SV}_k^{k\in 
-    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \qquad  	
-k\!\in\! K \qquad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
-\\
-\\     	
-	\forall m\!\!\in\!\! I_1\cup\{j_0\}. {\pNet_m 
-	\models\openrule
-    	{
-    	\beta_{j}^{j\in J_m}, \Pred_m, \Post_m}
-    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {\alpha_m}
-    		\ostate{(s_i^\prime)^{i\in L_m}}} }	
-  \qquad
-\forall m\!\!\in\!\! I_2.		{ \pNet_m 
-    	 \models
-    	\openrule
-    	{\emptyset, \Pred_m, \Post_m}
-    	{\ostate{s_m} \OTarrow {\alpha_m}
-    		\ostate{s_m'}} }\\\\
-     J'_{PQ}=  J\setminus\{j_0\}\uplus J_Q	\\
-    	\Pred\,'' =\bigwedge_{m\in I _1\uplus I_2}\Pred_m \land \Pred\,'
-\land \Pred(SV_k,v_i^{i\in I_1\uplus I_2}\uplus(j_0\mapsto v_Q),\beta_j^{j\in 
-J},\alpha)\\ 
-    	\forall i\in	L\backslash \left(\biguplus_{m\in I_1\cup\{j_0\}}\!\! L_m \uplus I_2\right).\,s'_i=s_i \\
-    \fresh(\alpha'_m,\alpha',\beta_j,\alpha) 
-    }
-    {\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle
-    	\models
-    	{\openrule
-    		{
-    		{\beta_j}^{j\in  J'_{PQ}}, \Pred\,'',  	\Post\uplus \Post\,'}
-    		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {\alpha}
-    			\ostate{(s_i^\prime)^{i\in L\uplus L_Q}}}
-    	}
-    }
-\end{mathpar}  
-\end{small}
-   This provides the desired conclusion.     \end{proof}
-
-Note that we also have the following lemma (trivial):
-
-\begin{lemma}[Open transition composition -- inactive]\label{lem-compose-2} ~\\	This lemma is the simple case where the pNet filling the hole is not involved in the transition.
-Suppose $j_0\not\in J$ and $L_Q=\Leaves({Q})$:\\[-2ex]
-\begin{mathpar}
-%\[
-P\models{\openrule
-	{
-		\beta_j^{j\in J}, 
-		\Pred,  
-		\Post}
-	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
-		\ostate{s_i'^{\, i\in L}}}
-}%\]
-\end{mathpar}
-Then, for any state $\ostate{s_i^{i\in L_Q}}$ of $Q$, we have\\[-1ex]
-	\[ P[Q]_{j_0}  
-	\models
-	{\openrule
-		{
-			\beta_j^{j\in J}, 
-			\Pred,  
-			\Post}
-		{\ostate{s_i^{i\in L}\uplus s_i^{i\in L_Q}} \OTarrow {\alpha}
-			\ostate{s_i'^{\, i\in L}\uplus s_i^{i\in L_Q}}}}
-	\]
-\end{lemma}
-The proof is trivial.
-
- \subsection{Proof of Theorem ~\ref{thm-congr-eq}}~\\
-\noindent{\bf  Congruence}:
-\textit{	Consider an open pNet:
-	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
-	\set{\symb{SV}}\myrangle$.
-	Let $j_0\in J$ be a hole. Let $\pNetQ$ and $\pNetQ'$ be two FH-bisimilar pNets such that 
-	$\Sortop(\pNetQ)=\Sortop(\pNetQ')=\Sort_{j_0}$\footnote{Note that $\Sortop(\pNetQ)=\Sortop(\pNetQ')$ is 
-	ensured by 
-	strong bisimilarity.}. Then 
-	$\pNet[\pNetQ]_{j_0}$ and 
-	$\pNet[\pNetQ']_{j_0}$ are FH-bisimilar.
-}
-\medskip
-\begin{proof}
- The proof of Theorem~\ref{thm-congr-eq} exhibits classically a bisimulation relation for 
- a 
- composed system.  It considers then an open transition of $P[Q]_{j_0}$ that should be 
- simulated. It then uses  Lemma~\ref{lem-decompose} to decompose the open transition 
- of $P[Q]_{j_0}$ and obtain an open transition of $P$ and $Q$; the FH-bisimulation 
- property can 
- be applied  to $Q$ to obtain an equivalent family of open transitions of $Q'$; this 
- family is 
- then recomposed by Lemma~\ref{lem-compose} to build a set of open transitions of 
- $P[Q']_{j_0}$ 
- that will simulate the original one.
-
- Let $\Leaves(Q)=p_l^{l\in L}$, $\Leaves(Q')={p'}_l^{l\in L'}$, 
- $\Leaves(P)=p_l^{l\in L_P}$.
- Consider $Q$ FH-bisimilar to $Q'$. It means that there is a relation 
- $\mathcal{R}$ that is an FH-bisimulation between the open automata of the two pNets. 
- We will consider the relation
-%\footnote{$\uplus$ is defined on sets as the disjoint union 
-% of the contained indexed 
-% sets} 
-$\mathcal{R}'=\{(s,t|\Pred_{s,t})|s=s'\uplus s'' \land 
- t=t'\uplus s'' \land s''\in \mathcal{S}_P \land (s',t'|\Pred_{s,t})\in\mathcal{R}\}$ 
-   where $\mathcal{S}_P$ is the set of states of the open automaton of $P$.	We will prove 
- that $\mathcal{R}'$ is an open FH-bisimulation. Consider a pair of FH-bisimilar 
- states: $(\ostate{s_{i}^{i \in L_P\uplus L}},\ostate{{t}_{i}^{i \in L'}\uplus 
- 	{s}_{i}^{i \in L_P}}|\Pred_{s,t})\in\mathcal{R}'$. %Those are states of the open 
- %	automata of 
- %	the pNets $P[Q]_{j_0}$ and $P'[Q]_{j_0}$. 
- Consider an 
- open transition $OT$ of $P[Q]_{j_0}$. %We need to find a family ${OT}_x^{x\in X}$ of 
- %	open transitions of $P'[Q]_{j_0}$ that satisfy the conditions of
- %	Definition~\ref{def-FH-bisim}. $OT$ is of the form 
- \\[-2ex]     
- \[P[Q]_{j_0}\models\openrule
- {
- 	\beta_j^{j\in J},\Pred_{OT},\Post_{OT}}
- { \ostate{s_{i}^{i \in L_P\uplus L}}\OTarrow {\alpha} \ostate{{s'}_{i}^{~i \in 
- 			L_P\uplus 
- 			L}}}\]
- Let $J'=J\setminus \Holes(Q) \cup \{j_0\}$.	 By 
- Lemma~\ref{lem-decompose} we have :\\[-2ex]
- 	\begin{mathpar}
- P\models{\openrule
- 	{
- 		\beta_j^{j\in J'}, 
- 		\Pred\,',  
- 		\Post\,'}
- 	{\ostate{s_{i}^{i\in L_P}} \OTarrow {\alpha}
- 		\ostate{s_{i}'^{\,i\in L_P}}}
- }\\
- Q\models{\openrule
- 	{
- 		\beta_j^{j\in J\cap\Holes(Q)}, \Pred\,'',  
- 		\Post\,''}
- 	{\ostate{s_{i}^{i\in L}} \OTarrow {\alpha_Q}
- 		\ostate{s_{i}'^{\,i\in L}}}
- }\end{mathpar}
- and  $\Pred_{OT}\iff \Pred\,'
- \land \Pred\,''\land \alpha_Q= \beta_{j_0}$, $\Post_{OT}=\Post\,'\uplus 
- \Post\,''$ ($\Post\,''$ is the restriction of $\Post$ over $\vars(Q)$). As $Q$ is FH-bisimilar to $Q'$ and $(\ostate{s_{i}^{i \in 
- 		L}},\ostate{{t}_{i}^{i \in L'}}|\Pred_{s,t})\in\mathcal{R}$ there is a family 
- $OT'_x$ 
- of 	open transitions of the automaton of $Q'$ such that\\[-2ex] 
- \begin{mathpar}
- Q'\models\openrule
- {
- 	\beta_{j x}^{j\in J\cap\Holes(Q)}, 
- 	\Pred_{OT_x},\Post_{OT_x}}
- {\ostate{t_{i}^{i\in L'}} \OTarrow {\alpha_x} \ostate{t_{i x}^{i\in L'}}}
- \end{mathpar}
- and  $\forall x, (\ostate{s_{i}^{i\in L}},\ostate{t_{i x}^{i\in 
- 		L'}}|\Pred_{s x})\in 
- \mathcal{R}$; 
- and  \\
- $\Pred_{s,t} \land \Pred\,''
- \implies$\\ $\displaystyle{\bigvee_{x\in X}
- \left( \forall j\in J\cap \Holes(Q). \beta_j\!=\!\beta_{jx}\!  \land\! 
- \Pred_{OT_x}
- \land \alpha_Q\!=\!\alpha_x \land  
- \Pred_{s, x}\subst{\Post\,''\uplus\Post_{OT_x}}\right)}$
-
- We can now apply Lemma~\ref{lem-compose} on each of the $OT'_x$ together with 
- the transition of $P$ and obtain a new family $OT_x$ of open transitions (where for 
- $i\in L_P$, $t_{i}=s_{i}$ and $t_{i x}=s'_{i}$, and for $j\in Holes(P)$, 
- $\beta_{j x}=\beta_j$):\\[-2ex]
- \[ P[Q']_{j_0}  
- \models
- {\openrule
- 	{
- 		\beta_{j x}^{j\in J}, 
- 		\Pred\,'\land\Pred_{OT_x}\land \alpha_x=\beta_{j_0 x} ,  
- 		\Post\,'\uplus \Post_{OT_x} }
- 	{\ostate{t_{i }^{i\in L'\uplus L_Q}} \OTarrow {\alpha_x}
- 		\ostate{{t}_{i x}^{i\in L'\uplus L_Q}}}
- }
- \]
-
- Observe that we used the fact that $J=(J\setminus\Holes(Q)\cup 
- \{j_0\})\setminus\{j_0\}\cup 
- (J\cap\Holes(Q))$. Now we have to verify the conditions for the 
- FH-bisimulation between $OT$ and $OT_x$.
- $\forall x, (\ostate{{s'}_{i}^{~i\in L_P\uplus L}},\ostate{t_{i 	x}^{i\in L_P\uplus L'}}|\Pred_{s, x})\in 
- \mathcal{R}'$ (by definition of
- $\mathcal{R}'$) and in three steps we get:
-
- \noindent                        
- \begin{small} $\Pred_{s,t} \land \Pred_{OT} 
- \implies 	\Pred_{s,t}\land\Pred\,'\land \Pred\,''\land\alpha_Q=\beta_{j_0}\\ % 
- 	%reversed 
- 	%substitution 
- 	\implies  \hspace{-2ex}
- 	{\displaystyle\bigvee_{x\in X}
- 	\left( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \land 
- 	\Pred_{OT_x}
- 	\land \alpha_Q\!=\!\alpha_x \land  
- 	\Pred_{s,x}\subst{\Post\,''\uplus\Post_{OT_x}}\right)\land
- }
- \\ \Pred\,'\land\alpha_Q=\beta_{j_0} \\
- 	\implies
- 	 \hspace{-2ex}
- 	{\displaystyle\bigvee_{x\in X}
- 		( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \land 
- 		\Pred\,'\land \Pred_{OT_x}
- 		\land \alpha_Q\!=\!\alpha_x \land \alpha_Q\!=\!\beta_{j_0 x}\, \land} \\ 
- 		\Pred_{s, x}\subst{\Post\,''\uplus\Post_{OT_x}})
- 	 $\end{small}
-
- Note that, $\beta_{j_0}$ can be transformed into  $\beta_{j_0 x}$ because of the 
- implication hypothesis.
- %\TODO{There was a confusion between the $\Rightarrow$ between the
- %  steps, and the $\implies$ inside the formulas...}
-% 
-% Explanations: first, we reversed the substitution; then we
-% restricted the 
-% substitution as $\beta_{j_0}$ only appears in $\Pred\,'$; then we
-% applied the property of FH-bisimulation for $P$ and rearranged the
-% terms using the fact that $v_Q=v_x$.
- The obtained formula reaches the goal except for 
- two points:
- \begin{itemize}
- 	\item We need $\forall j\!\in\! J$ instead of $\forall j\!\in\! J\cap\Holes(Q)$  but  
- 	adding prerequisite on more variables 
- 	does not   	change the validity of the formula (those variables are not used).
-\fussy
- 	\item Concerning the last term, we need 
- 	$\Pred_{s x}\subst{\Post_{OT}\uplus(\Post\,'\uplus \Post_{OT_x})}$, i.e.
- 	$\Pred_{s, x}\subst{(\Post\,'\uplus 	\Post\,'')\uplus(\Post\,'\uplus \Post_{OT_x})}$. We 
- 	can conclude by observing that	$\Pred_{s,x}$ does not use any variable of $P$ 
- 	and thus the substitution $\subst{Post\,'}$ has no effect on it.
-\sloppy
- \end{itemize}	
-Finally: \\
-\begin{small} $\Pred_{s,t} \land \Pred_{OT} \implies\\
-{\displaystyle\bigvee_{x\in X}
- 		\!\left( \forall j\in J. \beta_j=\beta_{jx} \! \land\! 
- 		\big(\Pred\,'\land\! \Pred_{OT_x}
- 		 \land \alpha_Q\!=\!\beta_{j_0 x}\right)\! \land\! \alpha_Q\!=\!\alpha_x\land\!  \Pred_{s, x}\subst{\Post\,''\!\uplus\!\Post_{OT_x}}\big)
- 		}$
- 		\end{small}\\
-This proves the  condition of the FH-simulation, the other direction is 
- similar.
-\end{proof}
-
-        \subsection{Proof of Theorem ~\ref{thm-ctxt-eq}: Context equivalence}
-\textit{	Consider two FH-bisimilar open pNets:
-	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
-	\set{\symb{SV}}\myrangle$ and 	$\pNet' = \mylangle {\pNet'}_i^{i\in I}, 
-	\Sort_j^{j\in 
-	J}, 	\set{\symb{SV'}}\myrangle$ 
-	(recall they must have the same holes to be bisimilar).
-	Let $j_0\in J$ be a hole, and $Q$ be a pNet such that $\Sortop(Q)=\Sort_{j_0}$. Then 
-	$\pNet[Q]_{j_0}$ and 
-	$\pNet'[Q]_{j_0}$ are FH-bisimilar.
-}
-
-\medskip
-
-\begin{proof}
-The proof of Theorem~\ref{thm-ctxt-eq} exhibits  a bisimulation relation for a 
-composed system. It then uses  Lemma~\ref{lem-decompose} to decompose the open transition 
-of $P[Q]_{j_0}$ and obtain an open transition of $P$ on which the FH-bisimulation 
-property can 
-be applied  to obtain an equivalent family of open transitions of $P'$; this family is 
-then recomposed by Lemma~\ref{lem-compose} to build a set of open transitions of 
-$P'[Q]_{j_0}$ 
-that will simulate the original one.
-
-        Let $\Leaves(Q)=p_l^{l\in L_Q}$, 
-$\Leaves(P)=p_l^{l\in L}$, $\Leaves(P')={p'}_l^{l\in L'}$.
-	Consider $P$ FH-bisimilar to $P'$. It means that there is a relation 
-	$\mathcal{R}$ that is an FH-bisimulation between the open automata of the two pNets. 
-	We will consider the relation $\mathcal{R}'=\{(s,t|\Pred_{s,t})|s=s'\uplus s'' \land 
-	t=t'\uplus s'' \land s\in \mathcal{S}_Q \land (s',t'|\Pred_{s,t})\in\mathcal{R}\}$ 
-	where $\mathcal{S}_Q$ is the set of states of the open automaton of $Q$.	We will prove 
-	that $\mathcal{R}'$ is an open FH-bisimulation. Consider a pair of FH-bisimilar 
-	states: $(\ostate{s_{1 i}^{i \in L\uplus L_Q}},\ostate{{s}_{2 i}^{i \in L'}\uplus 
-	{s}_{1 i}^{i \in L_Q}}|\Pred)\in\mathcal{R}'$. %Those are states of the open 
-%	automata of 
-%	the pNets $P[Q]_{j_0}$ and $P'[Q]_{j_0}$. 
-Consider an 
-	open transition $OT$ of $P[Q]_{j_0}$. %We need to find a family ${OT}_x^{x\in X}$ of 
-%	open transitions of $P'[Q]_{j_0}$ that satisfy the conditions of
-%	Definition~\ref{def-FH-bisim}. $OT$ is of the form 
-\\[-2ex]     
-	\[P[Q]_{j_0}\models\openrule
-	{
-		\beta_j^{j\in J},\Pred_{OT},\Post_{OT}}
-	{ \ostate{s_{i}^{i \in L\uplus L_Q}}\OTarrow {\alpha} \ostate{{s'}_{i}^{~i \in 
-	L\uplus 
-	L_Q}}}\]
-Let $J'=J\setminus \Holes(Q) \cup \{j_0\}$.	 By 
-	Lemma~\ref{lem-decompose} we have :\\[-2ex]
-			\begin{mathpar}
-				P\models{\openrule
-				{
-					\beta_j^{j\in J'}, 
-					\Pred\,',  
-					\Post\,'}
-				{\ostate{s_{1}^{i\in L}} \OTarrow {\alpha}
-					\ostate{s_{i}'^{~ i\in L}}}
-			}\\
-			Q\models{\openrule
-				{
-					\beta_j^{j\in J\cap\Holes(Q)}, \Pred\,'',  
-					\Post\,''}
-				{\ostate{s_{i}^{i\in L_Q}} \OTarrow {\alpha_Q}
-					\ostate{s_{i}'^{~ i\in L_Q}}}
-			}\end{mathpar}
-			and  $\Pred_{OT} \iff \Pred\,'
-		\land \Pred\,''\land \alpha_Q=\beta_{j_0}$, $\Post_{OT}=\Post\,'\uplus 
-			\Post\,''$ ($\Post\,''$ is the restriction of $\Post$ over $\vars(Q)$). As $P$ is FH-bisimilar to $P'$ and $(\ostate{s_{i}^{i \in 
-			L}},\ostate{{t}_{i}^{i \in L'}}|\Pred_{s,t})\in\mathcal{R}$ there is a family 
-			$OT'_x$ 
-			of 	open transitions of the automaton of $P'$ such that\\[-2ex] 
-			\begin{mathpar}
-			%    \left( fresh \ \set{a_i}, \set{b_j}, v_x.\ \
-			P'\models\openrule
-			{
-				\beta_{j x}^{j\in J'}, 
-				\Pred_{OT_x},\Post_{OT_x}}
-			{\ostate{t_{i}^{i\in L'}} \OTarrow {\alpha_x} \ostate{t_{i x}^{i\in L'}}}
-			%         \right)
-			\end{mathpar}
-			and  $\forall x, (\ostate{s_{i}^{i\in L}},\ostate{t_{i x}^{i\in 
-			L'}}|\Pred_{s x})\in 
-			\mathcal{R}$; 
-			and  \\
-			$\displaystyle{\Pred_{s,t} \land \Pred\,'
-		 \!\!\implies\!\!\! \bigvee_{x\in X}\!
-			\left( \forall j\in J'. \beta_j=\beta_{jx}\!  \land\! 
-			\Pred_{OT_x}\!
-			\land\! \alpha\!=\!\alpha_x\! \land\!  
-			\Pred_{s,x}\subst{\Post\,'\uplus\Post_{OT_x}}\right)}$
-			%     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x}) \right)$.
-
-			We can now apply Lemma~\ref{lem-compose} on each of the $OT'_x$ together with 
-			the transition of $Q$ and obtain a new family $OT_x$ of open transitions (where for 
-			$i\in L_Q$, $t_{i}=s_{i}$ and $t_{i x}=s'_{i}$, and for $j\in Holes(Q)$, 
-			$b_{j x}=b_j$):\\[-2ex]
-				\[ P'[Q]_{j_0}   
-				\models
-				{\openrule
-					{
-						\beta_{j x}^{j\in J}, 
-						\Pred_{OT_x} \land\Pred\,''\land\alpha_Q=\beta_{j_0 x},  
-						\Post_{OT_x}\uplus \Post\,''}
-					{\ostate{t_{ i }^{i\in L'\uplus L_Q}} \OTarrow {\alpha_x}
-						\ostate{{t}_{ i x}^{i\in L'\uplus L_Q}}}
-				}
-				\]
-			Observe that $J=(J\setminus\Holes(Q)\cup \{j_0\})\setminus\{j_0\}\cup 
-			(J\cap\Holes(Q))$. Now we have to verify the conditions for the 
-			FH-bisimulation between $OT$ and $OT_x$.
-			 $\forall x, (\ostate{{s'}_{i}^{~i\in L\uplus L_Q}},\ostate{t_{i 
-			x}^{~i\in L'\uplus L_Q}}|\Pred_{s, x})\in 
-			\mathcal{R}'$ (by definition of
-                        $\mathcal{R}'$) and in four steps we get:
-
-\noindent                        
-\begin{small} 
-$\Pred_{s,t} \land \Pred_{OT} \implies
- \Pred_{s,t}\land\Pred\,'\land \Pred\,''\land \alpha_Q=\beta_{j_0}\\  
- \implies  \hspace{-2ex}
-{\displaystyle{\bigvee_{x\in X}\!(\forall j\!\in\! J'. \beta_j\!=\!\beta_{jx}  
-\!\land \!
-\Pred_{OT_x}\!\land\! \alpha_Q\!=\!\beta_{j_0}
-\land\! \alpha\!=\!\alpha_x}} %\\ \hspace*{40mm} %
-\land \Pred_{s, x}\subst{\Post\,'\uplus\Post_{OT_x}}) \land
-\Pred\,''\\ % 
-			%FH for P
- \implies  \hspace{-2ex}
-	{\displaystyle{\bigvee_{x\in X}\!(\forall j\!\in\! J'. \beta_j\!=\!\beta_{jx}  
-\land \!
-\left(\Pred_{OT_x}\!\land\!
-\Pred\,''\!
-\land \alpha_Q\!=\!\beta_{j_0 x}\right)
-\land \alpha\!=\!\alpha_x}} 
-\land \Pred_{s,x}\subst{\Post\,'\uplus\Post_{OT_x}}) 	
-$\end{small}
-
-%\TODO{There was a confusion between the $\Rightarrow$ between the
-%  steps, and the $\implies$ inside the formulas...}
-
- The obtained formula reaches the goal except for two points:
-\begin{itemize}
-	\item We need $\forall j\!\in\! J$ instead of $\forall j\!\in\! J'$ with 
-	$J'\!=\!J\!\setminus\! \Holes(Q) \cup \{j_0\}$ but the formula under the quantifier 
-	does not depend on 
-	$b_{j_0}$ now (thanks to 
-	the substitution). Concerning $\Holes(Q)$, adding prerequisite on more variables 
-	does not 
-	change the validity of the formula (those variables are not used).
-	\item We need $\Pred_{s, x}\subst{\Post_{OT}\uplus(\Post_{OT_x}\uplus \Post\,'')}$, i.e.,
-	$\Pred_{s,x}\subst{(\Post\,'\uplus \Post\,'')\uplus(\Post_{OT_x}\uplus \Post\,'')}$. We 
-	can conclude by observing that	$\Pred_{s, x}$ does not use any variable of $Q$ 
-	and thus the substitution involving $\Post\,''$ has no effect.
-\end{itemize}	
-This proves the  condition of the FH-simulation, the other direction is 
-similar.
-\end{proof}
-
-       \section{Weak FH-bisimulation lemmas and proofs}
-
-We  define a quantified composition operator for effects, i.e. $\Post$ elements of the open transitions.
-We use ${\displaystyle \bigotimes_{i=n}^{0} \Post_i}$ to denote  $\Post_n\otimes .. \otimes \Post_0$. By convention ${\displaystyle \bigotimes_{i=-1}^{0} \Post_i}$ is the identity.
-
-\subsection{Weak bisimulation is an equivalence}\label{app-WFH-equiv}
-
-In this section, we first define two alternative definitions, one for weak open transition, one for for weak bisimulation.
-We use these two alternative definitions to show that weak bisimulation is an equivalence, we will also re-use these alternative definitions in the  proofs of the theorems in next sections.
-
-\begin{lemma}[Alternative definition of weak open transitions]
-\label{lem-rel-OT-WOT} Let $A = \mylangle J,\mathcal{S}, s_0,V_1,
-    \mathcal{T}\myrangle$ be an open automaton and $\mylangle J,\mathcal{S}, s_0,V_2,
-    \WT\myrangle$ be the
-weak open automaton derived from $A$.  The two following statements are equivalent
-%For any weak open transition $\symb{WOT} \in \WT$, there exists an open transitions $\symb{OT} \in \mathcal{T}$ such that:\\
-\begin{enumerate}
-\item Either $   
-\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'$; or \\ 
-there exist   $\set{\beta_{1i}}$, $\set{\beta_{2i}}$, and $\set{\beta_{3i}}$, $\Pred_{1i}$, $\Pred_{3i}$, $\Post_{1i}$, and  $\Pred_2$, $\Post_2$, $n\geq -1$, $m\geq -1$ s.t.\footnote{$n=-1$ (resp.
-$m=-1$) corresponds to the case where there is no $\tau$ transition before (resp.
-after) the transition $\alpha$.}:
-
-\begin{mathpar}
-%\mprset {vskip=.5ex}
-%\inferrule 
-\forall i \in [0..n].\openrule
-    {
-       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
-         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T} \quad \wedge
-\quad
-\openrule
-         {
-           \set{\beta_2},\Pred_2,\Post_2 }
-         {s_2 \OTarrow {\alpha} s'_2} \in \mathcal{T}
-\quad \wedge\\
-\forall i \in [0..m].\openrule
-         {
-           \set{\beta_{3i}},\Pred_{3i},\Post_{3i}    }
-         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}
- \end{mathpar}
-\item  there exist $\set{\gamma}$, $\Pred$, $\Post$ s.t.
- \begin{mathpar}
-%   \Longleftrightarrow  {
-\openrule
-         {
-           \set{\gamma},
-		\Pred, \Post
-				 } {s \OTWeakarrow {\alpha'} s'} \in\WT
-%}
-\end{mathpar}
-where\\
-$
-\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n}^{0}\Post_{1j}}}\\
-s=s_{10} \wedge s_{1(n+1)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
-\displaystyle{
-\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup}\\
-{}~\qquad \displaystyle{\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
-\\
-\Pred=\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=n}^{0}\Post_{1j}}\land\\ 
-{}~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}}\Big)\\
-\Post=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}
-$
-
-\end{enumerate}
-\end{lemma}
-
-\begin{proof} ($\Rightarrow$) We present an induction on $n$ and $m$, focusing on the incrementation on $n$: we prove that the property is valid for $m=-1$, $n=-1$ apply a first induction proof for going from $n$ to $n+1$, a similar induction can be applied to go from $m$ to $m+1$ (omitted).
-\begin{itemize}
-\item The base case there is one transition, so $n=-1$ and $m=-1$, we have:
-\begin{mathpar}
- % \mprset {vskip=.5ex}
-%\inferrule{
- \openrule
-         {
-           \set{\beta},\Pred,\Post}
-         {s \OTarrow {\alpha} s'} \in \mathcal{T}
-%}
-%}
-\end{mathpar} 
-by rule \WTDeux\ we can directly conclude the implication: 
- \begin{mathpar}
- % \mprset {vskip=.5ex}
-%\inferrule{
-% \openrule
-%         {
-%           \set{\beta},\Pred,\Post}
-%         {s \OTarrow {\alpha} s'} \in \mathcal{T}
-%}
-
-\openrule
-         {
-           \set{\beta},\Pred,\Post}
-         {s \OTarrow {\alpha} s'} \in \mathcal{T} \Rightarrow 
-{ \openrule
-         {
-           \vis{\set{\beta}}\!,\Pred,\Post
-				 } {s \OTWeakarrow {\alpha} s'} \in \WT
-}
-\end{mathpar} 
-\item For the inductive step, first we have by induction hypothesis that the formula holds for some lengths $m$ and $n$.
-Induction step is to infer that formula holds for transitions of length  $n+1$.
-We consider the case $n'=n+1$.
-We want to prove (1) $\Rightarrow$ (2) in the lemma, and in (1) we  focus on the case where there is a set of open transitions (this is the case: $s\neq s'$).
-In other words, we consider the sequence of ($n+m+4$) open transitions:
-\begin{mathpar}
-\Big(\forall i \in [0..n+1].\openrule
-    {
-       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
-         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T} \quad \wedge
-\quad
-\openrule
-         {
-           \set{\beta_2},\Pred_2,\Post_2 }
-         {s_2 \OTarrow {\alpha} s'_2} \in \mathcal{T}
-\quad \wedge\\
-~~\qquad\qquad\forall i \in [0..m].\openrule
-         {
-           \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
-         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}
-\Big) 
-\end{mathpar}
-
-By recurrence hypothesis we suppose that  (1) $\Rightarrow$ (2) holds for $n$ and $m$ (compared to the line above, we remove the first $\tau$ transition). We have:\\
-
-$
-%\mprset {vskip=.5ex}
-%\inferrule 
-\Big(\forall i \in [1..n+1].\openrule
-    {
-       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
-         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T} \,\wedge\,
-\openrule
-         {
-           \set{\beta_2},\Pred_2,\Post_2 }
-         {s_2 \OTarrow {\alpha} s'_2} \in \mathcal{T}
-\, \wedge\\
-{}~~\hspace{2.25cm}\forall i \in [0..m].\openrule
-         {
-           \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
-         {s_{3i} \OTarrow {\tau} s_{3(i+1)}}\! \in\! \mathcal{T}
-\Big)  \Rightarrow\!  {
-\openrule
-         {
-           \set{\gamma},
-		\Pred, \Post
-				 } {s'' \OTWeakarrow {\alpha'} s'} \in\WT
-}
-$
-where\\
-\begin{align*}
-s''=s_{10} &\wedge s_{1(n+2)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
-\alpha'=&\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\!\!\Post_{1j}}}\\
-\set{\gamma}=&\mybigdotcup_{i=1}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup\\
-& \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }\\
-\Pred=&\bigwedge_{i=1}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{1}\Post_{1j}}\land\\ 
-&\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}}\Big)\\
-\Post=&\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}
-\end{align*}
-
-We need to prove that   by adding the following open transition the implication remains true:
-\begin{mathpar}
- % \mprset {vskip=.5ex}
-%\inferrule{
- \openrule
-         {
-           \set{\beta_{10}},\Pred_{10},\Post_{10}}
-         {s_{10} \OTarrow {\tau} s_{11}} \in \mathcal{T}%}
-\end{mathpar}
-First by using rule \WTDeux~ we have:
-\begin{mathpar}
-
- \openrule
-         {
-           \set{\beta_{10}},\Pred_{10},\Post_{10}}
-         {s_{10} \OTarrow {\tau} s_{11}} \in \mathcal{T}
-\Rightarrow 
-{ \openrule
-       {
-           \vis{\set{\beta_{10}}}\!,\Pred_{10},\Post_{10}
-				 } {s_{10} \OTWeakarrow {\tau}s_{11}} \in \WT
-}
-\end{mathpar}
-
-On the other hand, by rule \WTUn~ we have the following weak open transition:
-\begin{mathpar}
- \openrule
-         {
-          \emptyset,\True,\Id(s')
-				 } {s' \OTWeakarrow {\tau} s'} \in \WT
-\end{mathpar}
-
-Finally by applying rule \WTTrois~on  the above weak open transitions:
-
-\begin{mathpar}
-\inferrule {\openrule
-       {
-           \vis{\set{\beta_{10}}}\!,\Pred_{10},\Post_{10}
-				 } {s_{10} \OTWeakarrow {\tau}s_{11}}\! \in\! \WT
-\\
-\openrule
-         {
-           \set{\gamma},
-		\Pred, \Post
-				 } {s'' \OTWeakarrow {\alpha'} s'}\! \in\!\WT
-\\
-\openrule
-         {
-          \emptyset,\True,\Id(s'')
-				 } {s' \OTWeakarrow {\tau} s'}\! \in\! \WT
-\\\\
-\set{\gamma''}= \vis{\set{\beta_{10}}} \dotcup \set{\gamma}\subst{\Post_{10}}\\
-\Pred\,''\!=\!\Pred_{10}\land\Pred\subst{\Post_{10}}\\\\%\land (\Pred_3\subst{\Post_2})\subst{\Post_{10}}
-\Post\,''=\Id(s'')\shortotimes\Post\shortotimes\Post_{10} \\ \alpha''=\alpha'\subst{\Post_{10}}
-}
-{
-\openrule
-         {
-          \set{\gamma''}, \Pred\,'',\Post\,''
-				 } 
-         {s_{10} \OTWeakarrow {\alpha''} s'} \in\!\WT
-} \WTTrois
-\end{mathpar}
-where we obtain the conclusion of the lemma, as required with the following assertions (derived from previous assertions):
-\begin{align*}
-s_{10}=s_{10} &\wedge s_{1(n+2)}=s_{2} \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
-\alpha''=&\alpha\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}\subst{\Post_{10}} = \alpha\subst{\bigotimes_{j=n+1}^{0}\Post_{1j}}\\
-\set{\gamma''}=&\mybigdotcup_{i=0}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup\\
-&\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }
-\\
-\Pred=&\bigwedge_{i=0}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{0}\Post_{1j}}\land\\ 
-&\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{0}\Post_{1j}}\Big)
-\\
-\Post=&\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{0}\Post_{1j}
-\end{align*}
-
-The right part of the disjunction, i.e.
-\begin{mathpar}
-\Big(\alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'\Big)
-\end{mathpar}
-is handled trivially by rule \WTUn. 
-\end{itemize}
-
-\noindent ($\Leftarrow$) We proceed by structural induction on the rules  building  the weak transition (as described in the original definition).
-The recurrence hypothesis being that the  the original definition implies the characterisation (1),with the conditions stated at the bottom of the theorem.
-We consider the different rules:
-
-\begin{itemize}
-\item Case rule \WTUn. We have:
-\begin{mathpar}
-{\openrule
-         {
-           \emptyset,\True,\Id(s)
-				 } {s \OTWeakarrow {\tau} s} \in \WT
-}
-\end{mathpar}
-We can directly conclude by the right part of the disjunction the following:\\
-
-$
-{ \openrule
-         {
-           \emptyset,\True,\Id(s)
-				 } {s \OTWeakarrow {\tau} s} \in\! \WT
-}\! \Rightarrow\! \Big(\alpha = \tau \wedge \set{\gamma}=\emptyset \wedge \Pred \!=\!\True \wedge \Post =\Id(s)\wedge s\!=\!s'\Big)
-$
-\item Case rule \WTDeux. We have:
-\begin{mathpar}
-\openrule
-         {
-           \set{\gamma},\Pred,\Post}
-         {s \OTWeakarrow {\alpha} s'} \in \WT \Rightarrow
-         \openrule
-         {
-           \set{\beta},\Pred,\Post}
-         {s \OTarrow {\alpha} s'} \in \mathcal{T}         
-\end{mathpar}
-where $\set{\gamma} = \vis{\set{\beta}}$.\\
-
-These two cases above prove the implication with $n=-1$ and $m=-1$.
-
-\item Case rule \WTTrois. We have:
-\begin{mathpar}
-\inferrule {\openrule
-         {
-           \set{\gamma_1},\Pred_1,\Post_1   }
-         {s \OTWeakarrow {\tau} s'} \in \WT
-\\
-\openrule
-         {
-           \set{\gamma_2},\Pred_2,\Post_2  }
-         {s' \OTWeakarrow {\alpha} s''} \in \WT
-\\
-\openrule
-         {
-           \set{\gamma_3},\Pred_3,\Post_3    }
-         {s'' \OTWeakarrow {\tau} s'''} \in\WT
-\\
-\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land \Pred_3\subst{\Post_2\shortotimes\Post_1}
-\\
-\set{\gamma}=\set{\gamma_1}\dotcup \set{\gamma_2}\subst{\Post_1}\dotcup\set{\gamma_3}\subst{\Post_2\shortotimes \Post_1}\\
-\alpha'=\alpha\subst{\Post_1}
-}
-{
-\openrule
-         {
-           \set{\gamma},
-		\Pred,
-				\Post_3\shortotimes{\Post_2}\shortotimes{\Post_1} }
-         {s \OTWeakarrow {\alpha'} s'''} \in\WT
-}
-\end{mathpar}
-
-%where 
-%$\set{\gamma}=\set{\gamma_1} \dotcup \set{\gamma_2} \dotcup \set{\gamma_3}$,
-%$\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}$, and $\Post= ({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K}$
-
-\begin{enumerate}
-
-\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau open transitions such $n_1=n+m+3$, hence by simplification we have (strictly speaking, by induction we might also have the case $\alpha=\tau\land\set \gamma=\emptyset\land \ldots$ but in this case, rule \WTUn~ allows us to obtain a similar reduction with $n_1=1$):
-\begin{mathpar}
-%\inferrule{
-\openrule
-         {
-           \set{\gamma_1},\Pred_1,\Post_1   }
-         {s \OTWeakarrow {\tau} s'} \in\! \WT 
-\Rightarrow \,
- \forall i \in [0..n_1].\openrule
-    {
-       \set{\beta_{1i}},\Pred_{1i},\Post_{1i}   }
-         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T}
-\end{mathpar}
-where \\
-$ 
-s=s_{10} \wedge s_{1{(n_1+1)}}\!=s',\quad
-\displaystyle{\set{\gamma_1}= \mybigdotcup_{i=0}^{n_1} \vis{\set{\beta_{1 i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1 j} } }} \\
-\Pred_1\!=\!\bigwedge_{i=0}^{n_1}(\Pred_{1i} \subst{\bigotimes_{j=i-1}^{0}\Post_{i j}} ), \quad \Post_1= \bigotimes_{i=n_1}^{0} \subst{\Post_{1i}} 
-$
-
-\item Similarly, a series of $m_1$ open transitions such that $m_1=n+m+3$   can be simplified as follows: 
-\begin{mathpar}
-%\inferrule{
-\openrule
-         {
-           \set{\gamma_3},\Pred_3,\Post_3   }
-         {s'' \OTWeakarrow {\tau} s'''} \in\! \WT
-\Rightarrow\, 
-\forall i \in [0..m_1].\openrule
-    {
-       \set{\beta_{3i}},\Pred_{3i},\Post_{3i}   }
-         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}        
-\end{mathpar}
-where
-\begin{mathpar}
-s''=s_{30}
-
-\land
-
- s_{3{(m_1+1)}}\!=s'''
-
-\land
-
-\displaystyle{\set{\gamma_3}= \mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{3 i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{3 j} } }}
-
-\land
-
-\Pred_3\!=\!\bigwedge_{i=0}^{m_1}(\Pred_{3i} \subst{\bigotimes_{j=i-1}^{0}\Post_{3 j}} )
-
-\land
-
- \Post_3= \bigotimes_{i=m_1}^{0} \subst{\Post_{3i}} 
-\end{mathpar}
-
-\item Concerning the middle reduction, by induction hypothesis there exists a set of open transitions in $\mathcal{T}$ such that:
-\begin{mathpar}
-\openrule
-         {
-           \set{\gamma_2},\Pred_2,\Post_2  }
-         {s' \OTWeakarrow {\alpha'} s''} \in\! \WT
-\Rightarrow 
-\bigg(\forall i \in [0..n_2].\openrule
-    {
-       \set{\beta_{2i}},\Pred_{2i},\Post_{2i}}
-         {s_{2i} \OTarrow {\tau} s_{2(i+1)}} \in \mathcal{T}  \wedge
-
-\openrule
-         {
-           \set{\beta'},\Pred\,',\Post\,' }
-         {s_2 \OTarrow {\alpha''} s_2'} \in \mathcal{T}
- \wedge
-\forall i \in [0..m_2].\openrule
-         {
-           \set{\beta_{2i}'},\Pred_{2i}^{\,\prime},\Post'_{2i}    }
-         {s_{2i}' \OTarrow {\tau} s_{2(i+1)}'} \in \mathcal{T}
-\bigg)         
-\end{mathpar}
-
-where
-\begin{align*}
-s'=s_{20} &\wedge s_{2(n_2+1)}=s_2 \wedge  s_2' = s_{20}' \wedge s_{2(m_2+1)}'=s''\\
-\alpha''=&\alpha'\subst{\bigotimes_{j=n_2}^{0}\Post_{2j}}\\
-\set{\gamma_2}=&\mybigdotcup_{i=0}^{n_2} \vis{\set{\beta_{2i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{2 j} } }  \dotcup  \vis{\set{\beta'}\subst{\bigotimes_{j=n_2}^{0}\Post_{2j}}} \dotcup\\
-&
- \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{2i}} \subst{\bigotimes_{j=i-1}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j=n_2}^{0}\Post_{2j}}}
-\\
-\Pred_2=&\bigwedge_{i=0}^{n_2}\Pred_{2i}\subst{\bigotimes_{j=i-1}^{0}\Post_{2j}}\land\Pred\,' \subst{\bigotimes_{j={n_2}}^{0}\Post_{2j}}\land\\ 
-&\Big(\bigwedge_{i=0}^{m_2}\Pred\,'_{2i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}}\Big)\\
-\Post_2=&\bigotimes_{j=m_2}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}
-\end{align*}
-
-\end{enumerate}
-~~\\
-Therefore, we can deduce that we have:
-\begin{mathpar}
-{ \openrule
-         {
-           \set{\gamma}\!,\Pred,\Post
-				 } {s \OTWeakarrow {\alpha} s'} \in \WT
-}
- \Rightarrow
-\bigg(\forall i\in [0..(n_1\!+\!n_2)].\openrule
-    {
-       \set{\beta_{4i}},\Pred_{4i},\Post_{4i}   }
-         {s_{4i} \OTarrow {\tau} s_{4(i+1)}} \in\mathcal{T} \wedge
-
-\openrule
-         {
-           \set{\beta'},\Pred\,',\Post\,' }
-         {s_2 \OTarrow {\alpha''} s_2'} \in \mathcal{T}
-\wedge\,
-\forall i \in [0..(m_1\!+\!m_2)].\openrule
-         {\set{\beta_{5i}},\Pred_{5 i},\Post_{5i}    }
-         {s_{5i}\OTarrow {\tau} s_{5({i+1})}}\in\mathcal{T}\bigg)  
-\end{mathpar}
-
-such that
-\begin{align*}
-s_{4i}=\begin{cases}
-			s_{1i} & \mbox{if }i<n_1\\
-			s_{2i-n_1} & \mbox{if }i\geq n_1
-	   \end{cases}
-&\qquad\qquad\qquad&
-s_{5i}=\begin{cases}
-			s_{3i} & \mbox{if }i<m_1\\
-s_{2i-m_1}' & \mbox{if }i\geq m_1
-	\end{cases}\\
-\end{align*}
-
- and similarly for $\Pred_{4i}$, $\Pred_{5i}$, $\Post_{4i}$, and $\Post_{5i}$.
-
-Also, we have the following assertions:
-\begin{align*}
-s\!=\!s_{40}& ~\wedge~s_{4(n_1+n_2+1)}\!=s_2 ~\wedge~s_2' = s_{50} ~\wedge~ s_{5(m_1+m_2+1)}\!=\!s'\\
-\alpha''=&\alpha\subst{\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}\\
-\set{\gamma}=&\mybigdotcup_{i=0}^{n_1+n_2} \vis{\set{\beta_{4i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{4 j} } }  \dotcup  \vis{\set{\beta'}\subst{\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}}\dotcup \\
-&\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta_{5i}}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{5i}\shortotimes\Post\,'\shortotimes\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4i}} }\\
-\Pred=&
-\bigwedge_{i=0}^{n_1+n_2}\!\!\Pred_{4i}\subst{\bigotimes_{j=i-1}^{0}\Post_{4j}}\land\Pred\,' \subst{\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\!\Post_{4j}}\land\\ 
-&\quad\bigwedge_{i=0}^{m_1+m_2}\Pred_{5i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{5j}\shortotimes\Post\,'\shortotimes\!\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\!\Post_{4j}}\\
-\Post=&\bigotimes_{j=m_1+m_2}^{0}\!\!\!\Post_{5j}\shortotimes\Post\,'\shortotimes\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\Post_{4j}
-\end{align*}
-
-This concludes the inductive step, showing  that the decomposition expressed by the $\Leftarrow$ direction of the lemma is always possible with the right side conditions. 
-\qedhere
-\end{itemize}
-\end{proof}
-
-\begin{lemma}[Alternative definition of weak bisimulation]\label{lem-alternative-weak-bisim} The definition of weak bisimulation given in Definition \ref{def-Weak-bisim} is equivalent to the following one:
-
-\fussy
- Let $A_1 = \mylangle J,\mathcal{S}_1, s_0, V_1,
-    \mathcal{T}_1\myrangle$ and $A_2 = \mylangle J,\mathcal{S}_2,t_0, V_2, \mathcal{T}_2 \myrangle$ be open automata; $\mylangle J,\mathcal{S}_1, s_0,V_1,
-    \WT_1\myrangle$ and $\mylangle J,\mathcal{S}_2,t_0, V_2, \WT_2\myrangle$ be the
-weak open automaton derived from $A_1$ and $A_2$ respectively.
-For any  states
-$s\in\mathcal{S}_1$ and
-$t\in\mathcal{S}_2$ such that $(s,t|\Pred_{s,t})\in\mathcal{R}$, we 
-   have:
-\sloppy
-\begin{itemize}
- \item  For any open transition $\symb{WOT}$ in $\WT_1$:
- \begin{mathpar}
-     \openrule
-         {
-           \gamma_j^{j\in J'},\Pred_{OT},\Post_{OT}}
-         {s \OTWeakarrow {\alpha} s'}
-
-\end{mathpar}
- there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {t \OTWeakarrow {\alpha_x} t_x}
-\end{mathpar}
- such that  $\forall x, J'=J_{x}, (s',t_x|\Pred_{s',x})\in \mathcal{R}$; 
- and  \\
-$\Pred_{s,t} \land \Pred_{OT}\!\implies\!
-\displaystyle{\bigvee_{x\in X}
-   \left( \forall j\in J_x.\gamma_j\!=\!\gamma_{jx}\!\land\! \Pred_{OT_x}
-     \land \alpha\!=\!\alpha_x \!\land\!  
-     \Pred_{s',x}\subst{\Post_{OT}\!\uplus\!\Post_{OT_x}}\right)}$
-
- \item  and symmetrically any open transition from $\symb{WOT}$ in $\WT_2$ can be 
-      covered by a set of weak transitions from $s$ in $\WT_1$.
- \end{itemize}
-
-\end{lemma}
-
-\begin{proof} Note that Definition \ref{def-Weak-bisim} is a particular case of the definition above, thus we only need to prove one direction of the equivalence between the two definitions, namely: \\
-($\Rightarrow$) We prove that Definition \ref{def-Weak-bisim} implies the definition above. In other words,
-suppose that $\Pred_{s,t}\in \mathcal{R}$ 
-%and for any open transition $OT$ in $\mathcal{T}_1$:
-% \begin{mathpar}
-%     \openrule
-%         {
-%           \beta_j^{j\in J},\Pred_{OT},\Post_{OT}}
-%         {s \OTarrow {\alpha} s'}
-%\end{mathpar}
-%there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
-% \begin{mathpar}
-%    \openrule
-%         {
-%           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-%         {t \OTWeakarrow {\alpha_x} t_x}
-%\end{mathpar}
-% such that  $\forall x, J_{x}=\{j\in J|\beta_j\neq\tau\}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
-% and  \\
-% $\Pred_{s,t} \land \Pred_{OT}\\
-% \implies\!\!\!\displaystyle{\bigvee_{x\in X}}
-%   \big(\forall j\in J_x. \vis{\beta_j}=\gamma_{jx}\Rightarrow \Pred_{OT_x}
-%     \land \alpha\!=\!\alpha_x\land  
-%     \Pred_{s',t_x}\subst{\Post_{OT}\shortotimes\Post_{OT_x}}\big)$\\
-and  suppose that the following statement holds:
-\begin{mathpar}
-     \openrule
-         {
-           \gamma_j^{j\in J'},\Pred_{OT},\Post_{OT}}
-         {s \OTWeakarrow {\alpha} s'} \in \WT_1
-
-\end{mathpar}
-Moreover, by using Lemma \ref{lem-rel-OT-WOT} we know that:
-\begin{mathpar}
-    \openrule
-         {
-           \gamma_j^{j\in J'},\Pred_{OT},\Post_{OT}}
-         {s \OTWeakarrow {\alpha} s'} \in \WT_1
-         \Rightarrow
-\bigg(\forall i \in [0..n].\openrule
-    {
-       \beta_{1ij}^{j\in J_1'},\Pred_{1i},\Post_{1i}   }
-         {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T}_1  \wedge
-\\{\qquad\qquad\qquad\qquad\qquad}
-\openrule
-         {
-           \beta_{2j}^{j\in J_2'},\Pred_2,\Post_2 }
-         {s_{20} \OTarrow {\alpha'} s_{21}} \in \mathcal{T}_1
- \wedge
-\forall i \in [0..m].\openrule
-         {
-           \beta_{3ij}^{j\in J_3'},\Pred_{3i},  \Post_{3i}  }
-         {s_{3i} \OTarrow {\tau} s_{3(i+1)}} \in \mathcal{T}_1
-\bigg)
-\end{mathpar}
-where
-\begin{align*}
-s=s_{10} &\wedge s_{1(n+1)}=s_{20} \wedge s_{21} = s_{30} \wedge s_{3(m+1)}=s'\\
-\alpha=&\alpha'\subst{\bigotimes_{j=n}^{0}\Post_{1j}}\\
-\gamma_j^{j\in J'}=&\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup\\
-&\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }
-\\
-\Pred_{OT}=&\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=n}^{0}\Post_{1j}}\land\\ 
-&\qquad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}}\Big)\\
-\Post_{OT}=&\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}
-\end{align*}
-
-For the sake of simplicity, we prove the rule in the  restricted case where $n$ and $m$ are equal to $0$, hence a single tau open transition will be considered on each side of the potentially visible one.
-The proof may be easily generalized to the multiple tau open transitions by using the same reasoning and \WTTrois~ rule.
-Consider each open transition separately:
-\begin{enumerate}
-\item For the first open transition in $\mathcal{T}_1$:
-\begin{mathpar}
-%\inferrule{
- \openrule
-    {
-       \beta_{1j}^{j\in J_1'},\Pred_1,\Post_1   }
-         {s_{10} \OTarrow {\tau} s_{11}}          
-\end{mathpar}
-by hypothesis we have $(s,t|\Pred_{s,t})\in\mathcal{R}$  and $s=s_{10}$.
-Thus, by  Definition \ref{def-Weak-bisim} we  can deduce there exist weak open transitions $\symb{WOT}_a^{a\in A} \subseteq \WT_2$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j a}^{j\in J_{a}}, \Pred_{OT_a},\Post_{OT_a}}
-         {t \OTWeakarrow {\alpha_{1 a}} u_a}
-\end{mathpar}
- such that  $\forall a, J_{a}=\{j\in J_1'|\beta_{1j}\neq\tau\},   (s_{11},u_a|\Pred_{s_{11},a})\in \mathcal{R}$ and \\
- $\Pred_{s,t} \land \Pred_1\implies\\
- \displaystyle{\bigvee_{a\in A}}
-  \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}\!=\!\gamma_{ja} \!\land\! \Pred_{OT_a}\!
-     \land\! \alpha_{1 a}\!=\!\tau \land  
-     \Pred_{s_{11},a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$
-
- Note that, because $\AlgE\cap\AlgA=\emptyset$  (actions and expressions are disjoint) and $\alpha_{1 a}\!=\!\tau$ we have 
-directly ($\alpha_{1 a}$ cannot be a variable, and cannot contain expressions/variables because $\tau$ has no parameter):
-\begin{mathpar}
-    \openrule
-         {
-           \gamma_{j a}^{j\in J_{a}}, \Pred_{OT_a},\Post_{OT_a}}
-         {t \OTWeakarrow {\tau} u_a}
-\end{mathpar}
-%and\\
-%$\Pred_{s,t} \land \Pred_1\\
-%\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
-%  \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a}
-%     \land    \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$
-%
-
-\item Concerning the middle open transition in $\mathcal{T}_1$:
- \begin{mathpar}
-     \openrule
-         {
-           \beta_{2j}^{j \in J_2'},\Pred_2,\Post_2 }
-         {s_{20} \OTarrow {\alpha'} s_{21}} 
-\end{mathpar}
-we have  $(s_{11},u_a|\Pred_{s_{11},a})\in \mathcal{R}$  and $s_{11}=s_{20}$. Again 
- by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{b}^{b\in B} \subseteq \WT_2$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j b}^{j\in J_{b}}, \Pred_{OT_{b}},\Post_{OT_{b}}}
-         {u_a \OTWeakarrow {\alpha_{2 b}} v_{b}}
-\end{mathpar}
-such that  $\forall b, J_{b}=\{j\in J_2'|\beta_{2j}\neq\tau\}, 
-(s_{21},v_{b}|\Pred_{s_{21},b})\in \mathcal{R}$; \\
- $\Pred_{s_{11},a} \land \Pred_2\implies\\
-\displaystyle{\bigvee_{b\in B}}
- \!\!  \left( \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}\land \Pred_{OT_{b}}\!\land \alpha'\!=\!\alpha_{2 b}\! \land\!  
-     \Pred_{s_{21},b}\subst{\Post_2\uplus\Post_{OT_{b}}}\right)$
-
-\item Similarly to the case 1, we consider the third  open transition in $\mathcal{T}_1$:
-     \begin{mathpar}
-%\inferrule{
- \openrule
-    {
-       \beta_{3j}^{j \in J_3'},\Pred_3,\Post_3   }
-         {s_{30} \OTarrow {\tau} s_{31}} \in \mathcal{T}          
-\end{mathpar}
-From previous case, we have $(s_{21},v_{b}|\Pred_{s_{21},b})\in \mathcal{R}$, and we have $s_{21}=s_{30}$. Then, by
- Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{a}^{c\in C} \subseteq \WT_2$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{jc}^{j\in J_{c}}, \Pred_{OT_{c}},\Post_{OT_{c}}}
-         {v_{b} \OTWeakarrow {\tau} w_{c}}
-\end{mathpar}
- such that  $\forall c, J_{c}= \{j\in J_3'|\beta_{3j}\neq\tau\}, 
-(s_{31},w_{c}|\Pred_{s_{31},c})\in \mathcal{R}$ and \\
- $\Pred_{s_{21},b} \land \Pred_3\implies %\\
-\displaystyle{\bigvee_{c\in C}}
-   \!\left( \forall j\in J_{c}. \vis{\beta_{3j}}\!=\!\gamma_{jc} \! \land\! \Pred_{OT_{c}}\!
-     \land\!  
-     \Pred_{s_{31},c}\subst{\Post_3\uplus\Post_{OT_{c}}}\right)$
-
-\end{enumerate}
-\medskip     
-Based on cases described above by applying \WTTrois~rule on the resulting $\symb{WOT}$s we have:
-
-\begin{mathpar}
-  \mprset {vskip=.5ex}
-\inferrule {
-\openrule
-         {
-           \gamma_{j a}^{j\in J_{a}}, \Pred_{OT_x},\Post_{OT_a}}
-         {t \OTWeakarrow {\tau} u_a}
-\qquad
-\openrule
-         {
-           \gamma_{j b}^{j\in J_{b}}, \Pred_{OT_{ y}},\Post_{OT_{b}}}
-         {u_a \OTWeakarrow {\alpha_2} v_{b}}
-\qquad
-\openrule
-         {
-           \gamma_{jc}^{j\in J_{c}}, \Pred_{OT_{c}}, \Post_{OT_{c}}}
-         {v_{b} \OTWeakarrow {\tau} w_{c}}
-\\ 
-\set{\gamma'}=\gamma_{j a}^{j\in J_{a}} \dotcup \gamma_{jb}^{j\in J_{b}} \subst{\Post_{OT_a}} \dotcup\gamma_{jc}^{j\in J_{c}} \subst{\Post_{OT_{ b}}\shortotimes\Post_{OT_a}}\\
-\Pred=\Pred_{OT_a}\land\Pred_{OT_{b}}\subst{\Post_{OT_a}}\land \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}\\
-\Post= \Post_{OT_{c}} \shortotimes \Post_{OT_{b}}\shortotimes\Post_{OT_{a}}\quad \alpha''=\alpha_{2}\subst{\Post_{OT_a}}\\
-}
-{
-\openrule
-         {
-           \set{\gamma},
-		\Pred, \Post}  
-         {t \OTWeakarrow {\alpha''} w_{c}} 
-} 
- \end{mathpar}
-It remains to be proven that the following statement holds:\\
-$\Pred_{s,t} \land \Pred\implies
- \displaystyle{\bigvee_{x\in X}} 
-  ( \forall j\in J. \gamma_j'=\gamma_{j}  \land \Pred
-     \land \alpha \!=\! \alpha'' \land  
-     \Pred_{s',x}\subst{\Post_{OT}\uplus\Post\,})$\\
-We have:\\
-$\Pred_{OT}= \Pred_1 \wedge \Pred_2\subst{\Post_1} \wedge \Pred_3\subst{\Post_2\shortotimes\Post_1}$\\
-$\Post_{OT}=\Post_3\shortotimes \Post_2\shortotimes\Post_1$\\
-Moreover, we have the following  statement:\\
-$\Pred_{s,t} \land \Pred_1\implies
- \displaystyle{\bigvee_{a\in A}}
- \! \! \left( \forall j\in J_a. \vis{\beta_{1j}}=\gamma_{ja}  \land \Pred_{OT_a}
-      \land  
-     \Pred_{s_{11},a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$\\
-With the conjunction of the predicate $\Pred_2\subst{\Post_1}$ on both sides of the implication, we get:
-\begin{multline*}
-(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies \\
- \bigvee_{a\in A}
-  \!\! ( \forall j\in J_a. \vis{\beta_{1j}}\!=\!\gamma_{ja}\!  \land\! \Pred_{OT_a}\! \land\!
-     \Pred_{s_{11},a}\subst{\Post_1\uplus\Post_{OT_a}}) \wedge \Pred_2\subst{\Post_1\uplus\Post_{OT_a}}  \hspace{-2ex}
-\end{multline*}
-Note that  on the right side of the implication we added  the substitution  of $\Post_{OT_x}$ without affecting the validity of the statement, because  the domain  of the substitution $\Post_{OT_x}$ is disjoint from the others.
-Hence a little rewriting gives:
-\begin{multline*}
-(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies\\
-\bigvee_{a\in A}
-\!\!   \left(\forall j\in J_a. \vis{\beta_{1j}}\!=\!\gamma_{ja}\land \Pred_{OT_a}
-     \!\land(\Pred_{s_{11},a}\wedge\Pred_2)\subst{\Post_1\uplus\Post_{OT_a}} \right)
-\end{multline*}
-
-By replacing the inner predicate $(\Pred_{s_{11},u_a}\wedge\Pred_2)$ by the conclusion of the  statement given in case 2,  the formula becomes: 
-\begin{multline*}(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies\\
-{\bigvee_{a\in A}}
-   \!\!(\forall j\in J_a. \vis{\beta_{1j}}\!\!=\!\gamma_{ja}  \land \Pred_{OT_a}
-      \land ({\bigvee_{b\in B}}(
-    \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}  \land \Pred_{OT_{b}}\!\land 
-    \alpha'\!=\!\alpha_{2 b} \land\\ \Pred_{s_{21},b}\subst{\Post_2\uplus\Post_{OT_{b}}})\subst{\Post_1\uplus\Post_{OT_a}})
-\end{multline*}
-
-This can be rewritten into:
-\begin{multline*}(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1} \implies\\
-{\bigvee_{a\in A}}\, {\bigvee_{b\in B}} 
-(\forall j\in J_a.
-\vis{\beta_{1j}}\!\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-\vis{\beta_{2j}}\!=\!\gamma_{jb}\subst{\Post_1\uplus\Post_{OT_a}}   \land\Pred_{OT_a} \land \\ \Pred_{OT_{b}} \subst{\Post_1\uplus\Post_{OT_a}} \land  (\alpha'\!=\!\alpha_{2 b}) \subst{\Post_1\uplus\Post_{OT_a}} \land \\ \Pred_{s_{21},b}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})
-\end{multline*}
-Since $Post_1$  does not act on $\gamma_{jb}$, nor on $ \Pred_{OT_{b}}$ and $  \alpha_{2}$.
-As well $\Post_{OT_a}$  does not act on $\alpha'$, nor on  $\beta_{2j}$ the formula can be simplified as follows:
-\begin{multline*}(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies\\
-\displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}} 
-(\forall j\in J_a.
-\vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-\vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jb} \subst{\Post_{OT_a}}  \land\Pred_{OT_a} \land \\ \Pred_{OT_{b}} \subst{\Post_{OT_a}} \land \alpha'\subst{\Post_1}=\alpha_{2 b} \subst{\Post_{OT_a}} \land\\ \Pred_{s_{21},b}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})\end{multline*}
-Finally, the conjunction with the term $\Pred_3\subst{\Post_2\shortotimes\Post_1}$ of the both sides of the implication and rewriting, we get:
-\begin{multline*}(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\implies \\
-\displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}} 
-(\forall j\in J_a.\vis{\beta^1_j}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-\vis{\beta_{2j}}\subst{\Post_1}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}\land \Pred_{OT_a}\land\\\Pred_{OT_{b}}\subst{\Post_{OT_a}} \land  \alpha'\subst{\Post_1}= \alpha_{2 b} \subst{\Post_{OT_a}} \land (\Pred_{s_{21},v_b} \land  \Pred_3)\\ \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{b}}\shortotimes\Post_{OT_a}})\end{multline*}
-Again note that because of the domain  of the substitution is independent from some predicates and expressions, we removed $\Post_1$ and  we  added the term $\Post_{OT_{b}}\shortotimes\,\Post_{OT_a}$ in the substitution of the right side of the implication.\\
-Finally, by replacing the predicate $(\Pred_{s_{21},b} \land  \Pred_3)$
-by the conclusion of the  implication given in case 3, we get:
-\begin{multline*}\Pred_{s,t} \land \underbrace{\Pred_1\land \Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}}_{\Pred_{OT}}\implies\\
- {\bigvee_{a\in A}}\, {\bigvee_{b\in B}}\, {\bigvee_{c\in C}} 
-(\forall\! j\in\! J_a.\vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \!\in\! J_{b}.\vis{\beta_{2j}\subst{\Post_{OT_a}}}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}  \land \\
- \forall j\!\in\! J_{c}. \vis{\beta_{3j} \subst{\Post_2\,\shortotimes\,\Post_1}} \!=\!\gamma_{jc} \subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}  \land\\
-   \underbrace{\Pred_{OT_a}\land\Pred_{OT_{b}} \subst{\Post_{OT_a}} \land 
-  \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}}_{\Pred} \land  \underbrace{\alpha'\subst{\Post_1}}_{\alpha}=\underbrace{\alpha_{2 b} \subst{\Post_{OT_a}}}_{\alpha''} \\\land \Pred_{s_{31},c}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{c}}\shortotimes \Post_{OT_{b}}\shortotimes\Post_{OT_a}}_{\Post}})
-\end{multline*}
-The three for all statements (on $J_a$, $J_b$ and $J_c$) can be concatenated using $\dotcup$, the list union lifted to indexed sets (if $\gamma=\gamma'$ and $\gamma''=\gamma'''$ then $\gamma\dotcup\gamma''=\gamma'\dotcup\gamma'''$).
-\begin{multline*}\forall j\in J_a\uplus J_b\uplus J_c.
-\vis{\beta_{1j}}\dotcup \vis{\beta_{2j}\subst{\Post_{OT_a}}}\dotcup \vis{\beta_{3j} \subst{\Post_2\shortotimes\Post_1}}=\\ ~\hspace{5.5cm} \gamma_{j a} \dotcup \gamma_{jb} \subst{\Post_{OT_a}}  \dotcup \gamma_{jc} \subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}
-\end{multline*}
-We have  $s_{31}=s'$, so can rewrite the formula:\\
-$\Pred_{s,t} \land \Pred_{OT}\implies
-\displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}}\, \displaystyle{\bigvee_{c\in C}} 
-(\forall j\in J.\gamma_j'=\gamma_j \land  \Pred \land \alpha=\alpha''  \land \Pred_{s',c}\subst{\Post_{OT}\uplus\Post\,}$\\
-
-All the combinations of elements in $A$, $B$, and $C$ provides a set $X$ of weak open transitions (each combination of one transition in $A$, one in $B$, and one in $C$ provides one weak open transition in the set $X$, i.e.
-each $x\in X$ corresponds to a triple $(a,b,c)\in A\times B\times C$); this defines a set of weak open transitions indexed over $X$;  each such open transition leads to a $w_c$ that we call $t_x$.
-This re-indexing allows us to conclude:\\
-$\Pred_{s,t} \land \Pred_{OT}\implies
- \displaystyle{\bigvee_{x\in X}} 
-(\forall j\in J.\gamma_j'=\gamma_j \land  \Pred \land \alpha=\alpha''  \land \Pred_{s',x}\subst{\Post_{OT}\uplus\Post\,}$\\
-\end{proof}
-
-%\begin
-\noindent{\bf Theorem~\ref{thm-weak-equiv}}. \emph{Weak FH-Bisimulation is an equivalence}.
- Suppose $\mathcal{R}$ 
-is a weak FH-bisimulation. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
-reflexive, symmetric and transitive.
-%\end{theorem}
-
-With the above lemma, we can use the same technique as for Theorem \ref{thm-equiv}  to prove that a weak FH-bisimulation is an equivalence.
-Indeed, we essentially use the same proof-scheme the main difference concerns  $\beta$ and  $\gamma$.
-Indeed, while the schema of the proof of transitivity was not directly applicable on the definition of weak bisimulation,  Lemma~\ref{lem-alternative-weak-bisim} provides a characterisation of weak bisimulation similar to the definition of strong bisimulation, and thus the same proof scheme is directly applicable.
-
-\subsection{Composition properties}\label{sec:app-composition}
-This section gives decomposition/composition lemmas and their proofs, these are the equivalent of the composition lemmas for open transitions, but applied to weak open automata.
-\begin{lemma}[Weak open transition decomposition]\label{lem-decomposeWOT} 
-	Let $\Leaves(Q)=pLTS_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
-	lemma imply that $Q$ is 
-	not a pLTS but a similar lemma can be proven for a pLTS $Q$}:
-	\[ P[Q]_{j_0}  
-		\models
-		{\openrule
-			{
-				\gamma_j^{j\in J}, \Pred,  
-				\Post}
-			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
-				\ostate{s_i'^{\, i\in L}}}
-		}
-	\]
-		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.  
-		 Then there exist $n$, $\Pred\,'$,  
-		$\Post\,'$,   and for all $p\in[0..n]$ there exist $\beta_p$, $\alpha_p$, $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
-		%\[
-		\begin{mathpar}
-		P\models{\openrule
-			{
-				\gamma_j^{j\in (J_p\setminus \Holes(Q)) \cup \{j_0\}}, 
-				\Pred\,',  
-				\Post\,'}
-			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
-				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
-		}%\]
-\text{\qquad and \qquad}\gamma_{j_0}=[\beta_0..\beta_n]
-	\vspace{-2.2ex}\\\text{and for all $p\in[0..n]$~~}
-		%\[
-		Q\models{\openrule
-			{
-				\gamma_{p j}^{j\in J_p}, \Pred_p,  
-				\Post_p}
-			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
-				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
-		}%\]
-\\
-		\text{such that~\qquad}  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) 
-\text{, }
- \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigotimes_{i=p-1}^{0}\Post_i}, \\
-{~\hspace{2cm}}\Pred \iff \Pred\,'
-		\land \!\!\bigwedge_{p=0}^n(\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i} = \beta_p\land \Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i} ),
-\\
-{~\hspace{2cm}}\Post=\Post\,' \uplus \bigotimes_{p=n}^0
-		\Post_p,   \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\
-		\end{mathpar} 
-where for any $p$, $\Post_p$ only acts upon  variables $\vars(Q)$.
-\end{lemma}
-
-\begin{proof} Suppose that we have: 
-\begin{mathpar}
- P[Q]_{j_0} \models \openrule
-			{
-				{\gamma_j^{j\in J}}, \Pred,  
-				\Post}
-			{\ostate{s_l^{l\in L}} \OTWeakarrow {\alpha}
-				\ostate{s_l'^{\, l\in L}}} 
-\end{mathpar}
-By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
-$ \forall p\! \in [0..m_1]\,		
-	P[Q]_{j_0}\!\models		
-\openrule
-    {
-       \set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
-         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$,  $\qquad  P[Q]_{j_0}	\models \openrule
-         {
-           \set{\beta_2},\Pred_2,\Post_2 }
-         {\ostate{t_l^{l\in L}} \OTarrow {\alpha'} \ostate{{t'}_l^{l\in L}}}
-$ 
-\\
-and 
- $\forall p \in [0..m_2] \,\, P[Q]_{j_0}\!\models \openrule
-         {
-           \set{\beta_{3p}},\Pred_{3p}, \Post_{3p}   }
-         {\ostate{u^{l\in L}_{pl}} \OTarrow {\tau} \ostate{u^{l\in L}_{(p+1)l}}}
-$\\
-where\\
-{\small \begin{align*}
-\forall l\in L.\,&s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l\\
-\alpha=&\alpha'{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}}\\
-\gamma_j^{j\in J}=&\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\! \Post_{1j}}}\dotcup\  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup  
-{\mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }}
-\\
-\Pred=&\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\land
-\bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
-\Post=&\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}
-\end{align*}}
-
-\noindent We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$:
-\begin{enumerate}
-\item For each open transition  $\symb{OT}_p$ in the form ($\set{\beta_{1p}}=\beta_{1pj}^{j\in J_{1p}}$):\\ 
-\[P[Q]_{j_0}\!\models		
-\openrule
-    {
-       {\beta_{1pj}^{j\in J_{1p}}},\Pred_{1p},\Post_{1p}   }
-         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}\] 
-If $Q$ moves then we obtain by Lemma \ref{lem-decompose}:\\
-\begin{small}$P\models{\openrule
-			{
-				(\beta_{1pj})^{j\in (J_{1p}\setminus \Holes(Q)) \cup \{j_0\}}, 
-				{\Pred\,'_{1p}},  
-				{\Post\,'_{1p}}}
-			{\ostate{s_{p l}^{l\in L\setminus L_Q}} \OTarrow {\tau}
-					\ostate{({s_{(p+1) l}})^{l\in L\setminus L_Q}}}
-		}%\]
-	\text{~~and~~} 
-		Q\models{\openrule
-			{
-				(\beta_{1pj})^{j\in J_{1p}\cap\Holes(Q)}, {\Pred\,''_{1p}},  
-				{\Post\,''_{1p}}}
-				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{1p}}
-				\ostate{s_{(p+1)l}^{l\in L_Q}}}
-				}\\%\]\\
-$
-\end{small}
-such that  \\
-$\Pred_{1p} \!\!\iff\!\!
-{\Pred\,'_{1p}}\land {\Pred\,''_{1p}}\land\alpha_{1p}\!=\!\beta_{1pj_0}$, $\Post_{1p}\!=\!{\Post\,'_{1p}}\uplus{\Post\,''_{1p}}$  where ${{\Post\,''_{1p}}}$ is the restriction of $\Post_{1p}$ over   $\vars(Q)$.\\
-Else $Q$ does not move and we have: \\
-\begin{small}
-$P\models{\openrule
-			{
-				(\beta_{1pj})^{j\in (J_{1p}\setminus \Holes(Q)) }, 
-				{\Pred\,'_{1p}},  
-				{\Post\,'_{1p}}}
-			{\ostate{(s_{p l})^{l\in L\setminus L_Q}} \OTarrow {\tau}
-				\ostate{({s}_{(p+1) l})^{l\in L\setminus L_Q}}}
-		}$~~and~~ $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}} $
-\end{small}
-\item Similarly, we have similar open transitions on states $u_{pl}$ (for the final $\tau$ transitions).
-
-\item Finally, for the open transition in the form ($\set{\beta_{2}}=\beta_{2j}^{j\in J_2}$):\\ 
-\[P[Q]_{j_0}	\models \openrule
-         {
-           \beta_{2j}^{j\in J_2},\Pred_2,\Post_2 }
-         {\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha'} \ostate{(t'_l)^{l\in L_Q}}}\]
-If $Q$ moves then we  obtain by Lemma \ref{lem-decompose}:\\
-\begin{small}$
-		P\models{\openrule
-			{
-				(\beta_{2j})^{j\in (J_2\setminus \Holes(Q)) \cup \{j_0\}}, 
-				{\Pred\,'_2},  
-				{\Post\,'_2}}
-			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha'}
-				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
-		}%\]
-	\,\text{~~and~~}
-	Q\models{\openrule
-			{
-				(\beta_{2j})^{j\in J_2\cap\Holes(Q)}, {\Pred\,''_2},  
-				{\Post\,''_2}}
-			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_{20}}
-				\ostate{t_l'^{\,l\in L_Q}}}
-		}%\]
-$
-\end{small}\\
-such that  $\Pred_2 \iff {\Pred\,'_2}
-		\land {\Pred\,''_2}\land \alpha_2=\beta_{2j_0}$, $\Post_2={\Post\,'_2}\uplus 
-		{\Post\,''_2}$ where ${\Post\,''_2}$ is the restriction of $\Post_2$ over variables  $\vars(Q)$.
-
-Else $Q$ does not move and we have \\
-$\begin{small} P\models{\openrule
-			{
-				(\beta_{2j})^{j\in (J_2\setminus \Holes(Q)) \cup \{j_0\}}, 
-				{\Pred\,'_2},  
-				{\Post\,'_2}}
-			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha'}
-				\ostate{(t_l)'^{\,l\in L\setminus L_Q}}}
-		}%\]
-	\,\text{~~and~~} \ostate{t_l^{l\in L_Q}} = 
-				\ostate{(t_l')^{\,l\in L_Q}} \end{small}$
-
-\end{enumerate}
-By using  Lemma \ref{lem-rel-OT-WOT}, and denoting $\displaystyle{J=\bigcup_{i=0}^{m_1}J_{1i}\cup J_2\cup \bigcup_{i=0}^{m_2}J_{3i}}$, we can conclude from cases (1), (2) and (3) that we have:
-\begin{mathpar}
-		P\models{\openrule
-			{
-				(\gamma_j')^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
-				\Pred\,',  
-				\Post'}
-			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha''}
-				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
-		}%\]
-\end{mathpar}
-where
-$\alpha''=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}}$\\
-On the other hand, we have:
-$\alpha=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}}\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,''_{1j}}}=\alpha''\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,''_{1j}}}$.\\
-As $\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,''_{1j}}}$ has no effect on variables of $P$ and thus on variables of $\alpha''$, so we have $\alpha=\alpha''$.
-\\
-{\small \begin{align*}
-\forall l\in L.\,&s_l=s_{0l} \wedge s_{(m_1+1)l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)l}=s'_l\\
-{(\gamma_j')}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}=&\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}}} \dotcup\\
-& \mybigdotcup_{i=0}^{m_2}
-\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}} }
-\\
-\Pred\,'=&\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}\land\\ 
-&\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}\\
-\Post'=&\bigotimes_{j=m_2}^{0}\!\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}
-\end{align*}}
-
-Note that for all $j\in J\setminus \Holes(Q)$, $\gamma_j' = \gamma_j$ because for all $l$ $\Post\,'_{1l}$ coincide with $\Post_{1l}$ on the variables of $\beta_{1ij}$, and similarly for $\Post\,'_2$ and $\Post\,'_{3l}$.
-%Concerning $\gamma'_{j_0}$ we have:
-%\[\gamma'_{j_0}=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{{\alpha_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}} \dotcup\\
-%~~\qquad \mybigdotcup_{i=0}^{m_2}
-%\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}} }\]
-
-We introduce the following predicate (we will need it for reasoning on the global predicate and will reason on it along the proof):\\
-$\begin{array}{l}\displaystyle{
-\Pred_\beta=\bigwedge_{p=0}^{m_1}(\beta_{1pj_0}=\alpha_{1p})\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}} \wedge (\beta_{2j_0}=\alpha_{20})\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}} \wedge \\\qquad\qquad
-\displaystyle{
-\bigwedge_{p=0}^{m_2}(\beta_{3pj_0}=\alpha_{3p})
-\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}}
-\end{array}$
-
-Concerning $Q$, we reduce the sequence of OTs to a path for which it moves in all steps.
-In other words, if $Q$ does not move at step $q$, then we have $\ostate{s_{q_l}^{l\in L_Q}} = \ostate{{s}_{(q+1) l}^{l\in L_Q}}$ , then we skip the state $\ostate{{s}_{(q+1) l}^{l\in L_Q}}$, i.e.
-we rename all the following states  $\ostate{s_{p l}^{l\in L_Q}}$ where $p\geq q+1$ into $\ostate{{s}_{(p-1) l}^{l\in L_Q}}$.
-Note that self-loops where $Q$ does an action but stays at the same state are not removed.
-We proceed in the same way  for states named $u$.
-To simplify the proof, we suppose that in case 3, $Q$  moves, else transition 3 of $Q$ should be skipped and the last $s_{p l}$ are equal to the first $u_{0 l}$.
-So we have: \\
-\begin{small}
-$\forall p\! \in\! [0..n_1]~ Q\models{\openrule
-			{
-				(\beta_{1pj}')^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{1p}}},  
-				{{\Post\,''_{1p}}}}
-				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{1p}}
-				\ostate{s_{(p+1)l}^{l\in L_Q}}}
-				}%\]
-,~~$  
-$ Q\models{\openrule
-			{
-				(\beta'_{2 j})^{j\in J\cap\Holes(Q)}, {\Pred\,''_2},  
-				{\Post\,''_2}}
-			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_{20}}
-				\ostate{t_l'^{\,l\in L_Q}}}
-		}%\]
-$
-and \\
-$\forall p \in [0..n_2]~ Q\models{\openrule
-			{
-				(\beta'_{3pj})^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{3p}}},  
-				{{\Post\,''_{3p}}}}
-				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha_{3p}}
-				\ostate{u_{(p+1)l}^{l\in L_Q}}}
-				}%\]
-$
-\end{small}
-\\ 
-such that $n_1 \leq m_1$ and $n_2 \leq m_2$.
-
-By renaming all state names ($s$, $u$ and $t$) with the same state name $v$. We have:
-
-$\forall p \in [0..(n_1\!+\!n_2\!+\!2)]\,\, Q\models{\openrule
-			{
-				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_p}},  
-				{{\Post\,''_p}}}
-				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha'_{p}}
-				\ostate{v_{(p+1)l}^{l\in L_Q}}}
-				}%\]
-$\\ 
-In this equation, and using case 1 above for all $k\in [0\ldots n_1]$ there is a $p\in [0..m_1]$ such that $\alpha_{1p}=\alpha'_k$ (following the re-indexing done in the removal of steps where $Q$ does not move), we know that $\Pred_{1p}$ contains the predicate $( \alpha_{1p}=\beta_{1 p j_0})$.
-Because $\beta_{1 p j_0}$ only contains variables of $P$ and $\alpha'_k$ only variables of $Q$, we have:
-\begin{equation*}
-\begin{split}
-(\alpha_{1p}=\beta_{1pj_0})\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}&\iff
-\alpha_{1p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,''_{1j}}
-= \beta_{1 p j_0}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,'_{1j}} \\
-&\iff\alpha'_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post\,''_{j}}= \beta_{1 p j_0}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,'_{1j}} 
-\end{split}
-\end{equation*}
-We can obtain similar equations for $\alpha'_{n_1+1}$ related with $\beta_{2 j_0}$ and the  $\alpha'_k$ for $k\geq n_1+2$ related with $\beta_{3 p j_0}$ for some $p$.
-Note that the substitutions are however more complex in the other cases.
-Overall we obtain (we skip here the details about the three cases 1, 2, and 3 above that all fall into the same equation because of the re-indexing we perform): 
-\begin{equation}\label{eqproofbeta}
-\Pred_\beta \iff \gamma_{j_0}=
-\vis{[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,''_{j}}|p\in[0..n_1+n_2+2]]}
-\end{equation}
-
-%, 2 and 3 above, we have for all $k\in [0\ldots n_1+n_2+2]$, then there is an action $\beta$ such that $\beta=\beta_{1p j_0}$ s.t.
-$j_0\in J_{1p}$, or $\beta=\beta_{2 j_0}$ with $j_0\in J_{2}$, or $\beta=\beta_{3p j_0}$ s.t.
-$j_0\in J_{3p}$, where $\beta=\alpha_k$, additionally the different $\beta$ are ordered by following the OTs, somehow performing the same re-indexing as  the removal of steps where $Q$ does not move above.
-Overall we have\footnote{under the assumption written above, i.e.
-that $Q$ moves in the middle OT, i.e.
-$j_0\in J_{2}$}:
-%\[ \Pred_* \implies
-%[\beta_{1 p j_0}|j_0\in J_{1p}]\dotcup [\beta_{2 j_0}] \dotcup [\beta_{3 p j_0}|j_0\in J_{3p}] = [\alpha_0..\alpha_{n_1+n_2+2}]
-%\]
-%
-%And thus \[\gamma_{j_0} = []\]
-
-Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha'_p$ some of them may be non-observable (they are $\tau$ transitions).
-By considering the sequence of $\tau$ and non-$\tau$ actions we split the sequence of actions into $n+1$ sub-sequences, such that each subsequence is a sequence of actions containing  only one observable action that will be named $\alpha_p$, and possibly many non-observable ($\tau$) ones.
-
-\begin{figure}
-\begin{center}
-\includegraphics[width=6cm]{XFIG/proof-explain}
-\end{center}\caption{Composition of the subsequences}\label{figproof}
-\end{figure}
-
- We can decompose each of the $n+1$ sub-sequences in the following way (see Figure~\ref{figproof}).
-For $k\in [0..n]$ the position of the $k^{\text{th}}$ visible action is  $n_k$.
-For $l\in [1..n]$,  $n'_l$ is any index between $n_{l-1}$ and $n_l$, additionally $n'_0=0$ and $n'_{n+1}=n_1+n_2+3$.
-We obtain $n+1$ sub-sequences  made of the following OTs, for all $k\in [0..n]$ :\\
-\begin{small}
-$\forall p\! \in\! [n'_{k}..(n_k\!-\!1)]~ Q\models{\openrule
-			{
-				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{p}}},  
-				{{\Post\,''_{p}}}}
-				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
-				\ostate{v_{(p+1)l}^{l\in L_Q}}}
-				}%\]
-,\quad
-Q\models{\openrule
-			{
-				\beta_{n_k j}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{n_k}}},  
-				{{\Post\,''_{n_k}}}}
-				{\ostate{v_{n_kl}^{l\in L_Q}} \OTarrow {\alpha'_{{n_k}}}
-				\ostate{v_{(n_k+1)l}^{l\in L_Q}}}
-				}%\]
-$
-\end{small}
-and\\
-\begin{small}
-$\forall p \in [(n_k\!+\!1)..(n'_{k+1}\!-\!1)]\,\, Q\models{\openrule
-			{
-				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred\,''_{p}}},  
-				{{\Post\,''_{p}}}}
-				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\tau}
-				\ostate{v_{(p+1)l}^{l\in L_Q}}}
-				}%\]
-$
-\end{small}
-\\ 
-Thereafter, by Lemma \ref{lem-rel-OT-WOT} we can deduce the following weak open transition:
-\begin{mathpar}
-Q\models{\openrule
-			{
-			(\gamma_{kj})^{j\in J\cap\Holes(Q)},  {{\Pred_k}},  
-				{{\Post_k}}}
-			{\ostate{v_{kl}^{l\in L_Q}} \OTWeakarrow {\alpha_{k}}
-				\ostate{(v_{kl}')^{l\in L_Q}}}
-		}%\]
-\end{mathpar}
-with:
-{\small
-\begin{align*}
-\forall l \in L_Q. &v_{kl}=v_{(n'_{k})l} \wedge v_{kl}'=v_{(n'_k)l}\\
-\alpha_k=&\alpha'_{n_k}{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}}\\
-{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=&{\mybigdotcup_{i=n'_{k}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}} \dotcup\\
-&\mybigdotcup_{i=n_k+1}^{n'_{k+1}-1}
-\vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}} \subst{\bigotimes_{l=i-1}^{n_k\!+\!1}\!\Post\,''_{l}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}} }\\
-\Pred_k=&\bigwedge_{i=n'_{k}}^{n_k\!-\!1}\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\Pred\,''_{n_k} \subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\\ 
-&\bigwedge_{i=n_k+1}^{n'_{k+1}-1}\!\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\!\Post\,''_{j}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{j}}
-\\
-\Post_k= &\bigotimes_{j=n'_{k+1}-1}^{n'_{k}}\!\!\Post\,''_{j}
-\end{align*}
-}
-
-\noindent Note that for all $k\in[0..n-1]$, $v_{kl}'=v_{(k+1)l}$,  $v_{0l}=s_{0l}=s_l$, and $v'_{nl}=v_{(n_1+n_2+3) l}=u_{(n_2+1) l} = s'_l$.
-
-\noindent By definition of $\Post_k$, we have $\displaystyle{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post\,''_{j} = \bigotimes_{j=k-1}^{0}\!\!\Post_{j}}$.
-%In this case, the number of weak open transitions
-%might not be exactly the number of open transitions that take part in the reduction but something smaller, thus the resulting set of weak open transitions could also be smaller.\\
-Consequently,  we have:
-\[\alpha'_{n_k}{\subst{\!\bigotimes_{j=n_k-1}^{0}\!\!\!\Post\,''_{j}}} =
-\alpha'_{n_k}\displaystyle{\subst{\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post''_{j}\otimes\!\!\!\bigotimes_{j=n'_{k}-1}^{0}\!\!\!\Post\,''_{j}}} = \alpha_k\displaystyle{\subst{\!\bigotimes_{j=n'_{k}-1}^{0}\!\!\!\Post\,''_{j}}} =
-\alpha_k\displaystyle{\subst{\!\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}}\]
-From equation~\ref{eqproofbeta}, we obtain the following equation (we recall that the actions $\alpha_k$ are the actions $\alpha'_{p}$ that are observable): 
-\begin{eqnarray*}
-\Pred_\beta &\iff& \gamma_{j_0}=
-\mybigdotcup_{p=0}^{p=n_1+n_2+2}
-\vis{\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}}\\
-%&\iff&\gamma_{j_0}=
-%\mybigdotcup_{p=0}^{p=n_1+n_2+2}
-%\vis{\alpha_{p}\subst{\bigotimes_{j=p-1}^{n'_p}\!\!\Post_{j}}\subst{\bigotimes_{j=n'_p-1}^{0}\!\!\Post_{j}}}\\
-%\vis{[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n_1+n_2+2]]}\\
-%&\iff& \gamma_{j_0}=
-%\vis{[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[1..n]]}\\
-&\iff& \gamma_{j_0}=
-[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n]]
-\end{eqnarray*}
-
-We need now to show that the set of WOT obtained above verifies the conditions of the lemma, i.e. it is a set of WOT of the form:
-\[	Q\models{\openrule
-			{
-				\gamma_{p j}^{j\in J_p}, \Pred_p,  
-				\Post_p}
-			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
-				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
-		}\]
-with
-\[  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) \qquad\text{trivial}\]
-\[ \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigotimes_{i=p-1}^{0}\Post_i)}\]
-Indeed we have:
-\begin{equation*}
-\begin{split}
-\gamma_j^{j\in J}=&\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!
-\Post_{1j}}}\dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup\\& \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }\\
-\end{split}\end{equation*}
-
-And thus, because $\beta_{pj}^{j\in J\cap \Holes(Q)}$ are equal to the concatenation of  $(\beta'_{1pj})^{j\in J\cap \Holes(Q)}$, $(\beta'_{2j})^{j\in J\cap \Holes(Q)}$, and $(\beta_{3pj}')^{j\in J\cap \Holes(Q)}$ (re-indexed because we skipped some transitions), and additionally $(\beta_{1pj}')^{j\in J\cap \Holes(Q)}$, $(\beta_{2j}')^{j\in J\cap \Holes(Q)}$, and $(\beta_{3pj}')^{j\in J\cap \Holes(Q)}$ are identical to the hole labels $\beta_{1kj}^{j\in J\cap \Holes(Q)}$, $\beta_{2j}^{j\in J\cap \Holes(Q)}$, and $\beta_{3kj}^{j\in J\cap \Holes(Q)}$ (re-indexed) when $Q$ moves\footnote{more precisely, when $Q$ moves either $\beta_{1kj}^{j\in J\cap \Holes(Q)}$ is not empty  and thus $(\beta_{1pj}')^{j\in J\cap \Holes(Q)}=\beta_{1kj}^{j\in J\cap \Holes(Q)}$, or both are empty if the holes of $Q$ perform no action}.
-We can assert a similar equality on post-conditions, i.e.
-between $\Post\,''_p$ and $\Post\,''_{1k}$, $\Post\,''_{2}$, $\Post\,''_{3k}$ where $\Post\,''_{1p}$ is the restriction of $\Post_{1p}$ over $\vars(Q)$ (see initial decomposition, case 1, 2, and 3 above).
-Overall, we have
-$\forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i$ (see above):\\
-{\scriptsize \begin{equation*}
-\begin{split}
-\gamma_j^{j\in J\cap \Holes(Q)}&=\mybigdotcup_{i=0}^{m_1} \vis{\set{(\beta_{1i}')}\subst{\bigotimes_{j=i-1}^{0}\!\!
-\Post''_{1j}}}\dotcup  \vis{\set{\beta'_2}\subst{\bigotimes_{j=m_1}^{0}\Post''_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}} }\\
-&=\mybigdotcup_{k=0}^n \left( \mybigdotcup_{i=n'_k}^{n'_{k+1}-1}\vis{\beta_{ij}^{j\in J\cap \Holes(Q)}\subst{\bigotimes_{j=i-1}^{n'_k}\!\!\Post''_{j}\bigotimes_{j=n'_k-1}^{0}\!\!\Post''_{j}}}\right)\\
-&=\mybigdotcup_{k=0}^n \left( \gamma_{kj}^{j\in J\cap \Holes(Q)}\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{k}}\right)
-\end{split}\end{equation*}
-}
-Next, we have
-\[\Pred = \displaystyle{\Pred\,'
-		\land \!\!\bigwedge_{p=0}^n\Big((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i}) = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i}) \Big)}\]
-Indeed,
-\begin{scriptsize}
-\begin{align*}
-\Pred&\iff\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\land
-\bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
-&\iff\bigwedge_{i=0}^{m_1}\left(\Pred\,'_{1i}
-		\land {\Pred\,''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}\right)\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}} \\
-&\qquad\land\left(\Pred\,'_{2}
-		\land {\Pred\,''_{2}}\land \alpha_{20}=\beta_{2j_0}\right)\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
-&\qquad\land\bigwedge_{i=0}^{m_2} \left(\Pred\,'_{3i}
-		\land {\Pred\,''_{3i}}\land \alpha_{3i}=\beta_{3ij_0}\right) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\displaybreak[0]\\
-&\iff\bigwedge_{i=0}^{m_1}\left((\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{1j}})
-		\land ({\Pred\,''_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,''_{1j}})\land (\alpha_{1i}=\beta_{1ij_0})\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\right) \\
-&\qquad\land \left(\Pred\,'_{2}\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}
-		\land {\Pred\,''_{2}} \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \land (\alpha_{20}=\beta_{2j_0})\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \right) \\
-&\qquad\land\bigwedge_{i=0}^{m_2} \Bigg(\Pred\,'_{3i} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} 
-		\land {\Pred\,''_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}  \\
-		 & \qquad \land (\alpha_{3i}=\beta_{3ij_0}) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\Bigg)  \\
-&\iff \Pred\,'\land\bigwedge_{k=0}^n\Pred_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}\land\Pred_\beta
-\\&\iff \Pred\,'\land\bigwedge_{k=0}^n\Pred_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}\land
-(\gamma_{j_0}=[\alpha_{i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{j}}|i\in[0..n]])
-\end{align*}
-\end{scriptsize}
-which is exactly what is needed with $\gamma_{j_0}=[\beta_0..\beta_n]$.
-
-Finally we have~~
-$\Post=\displaystyle{\Post\,' \uplus \bigotimes_{p=n}^0
-		\Post_p}$\quad
-because
-{\small \begin{align*}
-\Post&=\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}\\
-&=\bigotimes_{j=m_2}^{0}\!\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j} \uplus \bigotimes_{j=m_2}^{0}\!\!\Post\,''_{3j}\shortotimes\Post\,''_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,''_{1j}\\
-&=\Post\,' \uplus \bigotimes_{j=n'_{n+1}-1}^{0}\!\!\Post\,''_{j}
-\end{align*}}
-Which concludes because we have we have $\displaystyle{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post\,''_{j} = \bigotimes_{j=k-1}^{0}\!\!\Post_{j}}$.
-%
-%Consequently, we have $n$ weak open transitions  $\symb{WOT}_k$ such that $k\in [1..n]$.
-%Therefore, we can conclude that we have for all $k\in [1..n]$:  
-%\begin{mathpar}
-%Q\models{\openrule
-%			{
-%			\gamma_{kj}^{j\in J_k}, {\Pred_k}, {\Post_k}}
-%			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha'_{k}}
-%				\ostate{s_{(p+1)l}^{l\in L_Q}}}
-%		}%\]
-%\end{mathpar}
-%
-%%By considering $n=m_1+m_2+2$,  and $\forall p \in [0..n]$: \\
-%%$\Pred_{p}= \left\{
-%% \begin{array}{ll}
-%%\Pred_{1p} & \mbox{if }p<m_1\\
-%%\Pred_{2} & \mbox{if } p=m_1\\
-%%\Pred_{1(p-m_1)} & \mbox{if }p\geq m_1\\
-%%\end{array}
-%%\right. 
-%%\quad$
-%% $\qquad
-%%\Post_{p}= \left\{
-%% \begin{array}{ll}
-%%\Post_{1p} & \mbox{if }p<m_1\\
-%%\Post_{2} & \mbox{if } p=m_1\\
-%%\Post_{1(p-m_1)} & \mbox{if }p\geq m_1\\
-%%\end{array}
-%%\right. 
-%%$\\
-%%and similarly for $\beta_p$. Thus, we can rewrite $\gamma$ given in the hypothesis as: \\
-%%$\set{\gamma}= \displaystyle{\mybigdotcup_{p=0}^{n}
-%%\vis{\set{\beta_{p}}}\subst{\bigotimes_{p=n}^{0} \Post_{p}}}$\\
-%Furthermore, still by hypothesis we have:\\
-%$\Pred=\displaystyle{\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }\land \\
-%~\qquad \quad \bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}$\\
-%By replacing $\Pred_{1i}$,  $\Pred_2$, and $\Pred_{3i}$ by their equivalent formula obtained from cases 1, 2 and 3 we have:\\
-%$\Pred =\displaystyle{\bigwedge_{i=0}^{m_1}({\Pred'_{1i}}
-%		\land {\Pred''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}) \bigotimes_{j=i-1}^{0}\subst{\Post_{1j}}\land}\\
-%~~\qquad\qquad({\Pred'_2}\land {\Pred''_2}\land \alpha_2=\beta_{2j_0})	\bigotimes_{i=m_1}^{0}\subst{\Post_{1i}}\land\\
-%~~\qquad\qquad\bigwedge_{i=0}^{m_2} ({\Pred'_{3i}}\land {\Pred''_{3i}}\land \alpha_{3i}=\beta_{3ij_0})
-%\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}$\\
-%By distribution of the substitution operation over the logical operator we reformulate as:\\
-%$\Pred= \displaystyle{\big(\bigwedge_{i=0}^{m_1}
-%{\Pred'_{1i}}\bigotimes_{j=i-1}^{0}\subst{{\Post'_{1j}}}\big)
-%\land{\Pred'_2}\bigotimes_{i=m_1}^{0}\subst{{\Post'_{1i}}}\land} \\
-%~~\qquad\qquad\bigwedge_{i=0}^{m_2}{\Pred'_{3i}}\bigotimes_{j=i-1}^{0}\subst{{\Post'_{3j}}}\subst{{\Post'_2}}\bigotimes_{j=m_1}^{0}\subst{{\Post'_{1j}}} \land\\	
-%~\qquad\qquad\bigwedge_{i=0}^{m_1}({\Pred''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}) \bigotimes_{j=i-1}^{0}\subst{\Post_{1j}}\land({\Pred''_2}\land \alpha_2=\beta_{2j_0})	\bigotimes_{i=m_1}^{0}\subst{\Post_{1i}}\land\\
-%~\qquad\qquad\bigwedge_{i=0}^{m_2} ({\Pred''_{3i}}\land \alpha_{3i}=\beta_{3ij_0})\bigotimes_{j=i-1}^{0}\subst{\Post_{3j}}\subst{\Post_2}  \bigotimes_{i=m_1}^{0}\subst{\Post_{1i}}
-%$\\		
-%Thus, we can write the formula as follows:\\
-%$\Pred= \Pred\,' \wedge \displaystyle{\bigwedge_{p=0}^{n}}((\alpha_p= \beta_{pj_0}\land \Pred_p)\bigotimes_{i=p-1}^{0}\Post_i)$\\
-%We proceed the same way with the postcondition,  we have:\\
-%$\Post=\displaystyle{\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}$\\
-%By replacing ${\Post_{1i}}$,  $\Post_2$, and ${\Post_{3i}}$ their values obtained from the cases 1, 2, and 3, and because the ${\Post'_i}$ and ${\Post''_i}$ are independent (the ${\Post'_i}$ concern the leaves of $P$ while the ${\Post''_i}$ concern the leaves of $Q$), we obtain:\\
-%$\Post= \displaystyle{\bigotimes_{i=m_2}^{0}\subst{{\Post'_{3i}}\uplus 
-%		{\Post''_{3i}}} \subst{{\Post'_2}\uplus 
-%		{\Post''_2}} \bigotimes_{j=m_1}^{0}\subst{ {\Post'_{1i}}\uplus 
-%		{\Post''_{1i}}}}\\
-%~~\qquad= \bigotimes_{i=m_2}^{0}{\Post'_{3i}}\subst{{\Post'_2}}\bigotimes_{j=m_1}^{0}\subst{{\Post'_{1j}}} \uplus \bigotimes_{i=m_2}^{0}{\Post''_{3i}}\subst{{\Post''_2}}\bigotimes_{j=m_1}^{0}\subst{{\Post''_{1j}}} \\
-%~~\qquad= \Post' \uplus \bigotimes_{j=n}^{0} \Post_j $\\
-%\qed
-\end{proof}
-
-\begin{lemma}[Weak open transition composition]\label{lem-Weakcompose1} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
-	Suppose $j_0\in J$  and:\\[-1ex]
-\begin{mathpar}
-%\[
-P\models{\openrule
-	{
-		\beta_j^{j\in J}, 
-		\Pred,  
-		\Post}
-	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
-		\ostate{(s_i')^{\, i\in L}}}
-}
-\quad\text{~~and~~}\quad
-Q\models{\openrule
-	{
-		\set{\gamma},
-		 \Pred_Q,  
-		\Post_Q}
-	{\ostate{s_{i}^{i\in L_Q}} \OTWeakarrow {\alpha_Q}
-		\ostate{(s'_{i})^{\, i\in L_Q}}}
-}%\]
-\end{mathpar}
-
-Let 
-%J_Q=\displaystyle{\bigcup_{t=0}^nJ_{t}}
-\qquad
-$\Pred\,'=\Pred\land (\beta_{j_0}=\alpha_Q\land \Pred_Q) \quad\text{~~and~~}\quad
-%\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
-\Post\,'=\Post\uplus\Post_Q
-$
-
-Then, we have
-{\small	\[ P[Q]_{j_0}  
-	\models
-	{\openrule
-		{
-			\set{\gamma}\uplus\vis{\beta_j^{j\in J\setminus \{j_0\}}}, 
-			\Pred\,',  \Post\,'
-			 }
-		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
-			\ostate{(s_i')^{\, i\in L\uplus L_Q}}}
-	}
-	\]}
-\end{lemma}
-\begin{proof}
-By  Lemma \ref{lem-rel-OT-WOT} we can decompose the WOT of $Q$ into  a series of $k+1$ and $k'+1$ tau open transitions and an $\alpha'_Q$ open transition (observable or not depending on $\alpha_Q$):
-\begin{mathpar}
-\forall h\!\in\![0..k].Q\models\openrule
-    {\set{\beta_{1h}},\Pred_{1h},\Post_{1h}   }
-         {\ostate{{(s_{1h})}} \OTarrow {\tau} \ostate{{(s_{1(h+1)})}}}, \quad
-Q\models{\openrule
-	{
-		\set{\beta_2},
-		 \Pred_2,  
-		\Post_2}
-	{\ostate{s_{20}}\OTarrow {\alpha'_Q}
-		\ostate{s_{21}}}
-}, \\ \quad\text{~~and~~}\quad 
-\forall h \in [0..k'].Q\models\openrule
-         {
-           \set{\beta_{3h}},\Pred_{3h}, \Post_{3h}}
-         { \ostate{(s_{3h})} \OTarrow {\tau} \ostate{(s_{3(h+1)})}}
-\end{mathpar}
-such that\\
-
-\begin{small}
-$s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$
-\begin{align*}
-\alpha_Q=&\alpha'_Q\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}\\
-\set{\gamma}=&\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{j=h-1}^{0}\!\! \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=k}^{0}\Post_{1j}}} \dotcup%\\
-		%&
- \mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{j=h-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=k}^{0}\Post_{1j}} }\\
-\Pred_Q=&\bigwedge_{h=0}^{k}\!\Pred_{1h}\subst{\!\bigotimes_{j=h-1}^{0}\!\!\!\Post_{1 j}}\land \Pred_2\subst{\bigotimes_{h=k}^{0}\!\Post_{1h}}\land%\\
-%&
-	\!\bigwedge_{h=0}^{k'}\!\Pred_{3h}\subst{\!\! 	\bigotimes_{j=h-1}^{0}\!\!\!{\Post_{3j}}\otimes{\Post_2}  \otimes\bigotimes_{h=k}^{0}\!\!\Post_{1h}}\\
-\Post_Q=&\bigotimes_{h=k'}^{0}\!\!\Post_{3h}\otimes\Post_2\otimes\bigotimes_{j=k}^{0}\!\!\Post_{1j}
-\end{align*}
-
-\end{small}
-\begin{enumerate}
-
-\item For the first $k$ open tau transitions, by Definition \ref{def:Non-ObsTau} $P$ can necessarily make a tau open transition if the hole indexed $j_0$ makes a tau action.
-So by Lemma \ref{lem-compose} we obtain $k$ open transitions in the form:
-\[P[Q]_{j_0}\!\models		
-\openrule
-    {
-       \set{\beta_{1h}},{\Pred_{1h}},{\Post_{1h}}   }
-         {\ostate{s_{1h}\uplus s^{i\in L}_{i} } \OTarrow {\tau} \ostate{s_{1(h+1)}\uplus s^{i\in L}_{i}}}\]
-
-\item For the possibly observable open transition.  By Lemma \ref{lem-compose} with the lemma hypotheses we obtain:\\ 
-	\[ P[Q]_{j_0}  
-	\models
-	{\openrule
-		{
-			{\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2}, 
-			\Pred\land\Pred_2\land \alpha_Q=\beta_{j_0 },  
-			\Post\uplus \Post_2}
-{\ostate{s^{i\in L}_{i}\uplus s_{20}} \OTarrow {\alpha} \ostate{{s'}^{i\in L}_{i}\uplus s_{21}}}
-	}
-	\]
-
-%
-%\[P[Q]_{j_0}\!\models		
-%\openrule
-%    {
-%       {\beta^i_{p j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2},{\Pred_p}\!\!'',{\Post_p}\!\!''   }
-%         {\ostate{s^{i\in L \uplus L_Q}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L\uplus L_Q }_{(p+1)i}}}\] \\
-% such that  ${\Pred_p}\!\!'' \iff {\Pred_p}
-%		\land {\Pred_p}\!\!'\land \alpha_t=\beta_{j_0}$, ${\Post_p}\!\!''={\Post_p}\uplus 
-%		{\Post_p}\!\!'$\\ 
-\item We proceed in the same way as the first item for $k'$ last weak open transitions, and we obtain $k'$ open tau transitions.
-\end{enumerate}
-
-Using Lemma \ref{lem-rel-OT-WOT}, from cases $(1)$, $(2)$ and $(3)$ we get: 
-\[P[Q]_{j_0}\!\models		
-\openrule
-    {
-\set{\gamma_c}, \Pred_c,
-\Post_c}
-         {\ostate{s_{10}\uplus s^{i\in L}_{i}} \OTWeakarrow {\alpha'} 
-	\ostate{{{s'}^{i\in L}_{i}\uplus s_{3(k'+1)}}}}\] 
-where ~~
-$\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$
-and $\alpha=\alpha'$  because $\Post_{1j}$ acts on variables of $Q$ and $\alpha$ contains only variables of $P$.
-\begin{small}
-\begin{align*}
-\set{\gamma_c}=&\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{i=h-1}^{0}\!\!
-\Post_{1i} } }  \dotcup  \vis{({\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2})\subst{\bigotimes_{i=k}^{0}\Post_{1i}}} \dotcup\\
-&\mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{i=h-1}^{0}\!\!\Post_{3i}\shortotimes\Post_2\shortotimes\bigotimes_{i=k}^{0}\Post_{1i}} }\\
-=&\set{\gamma}\uplus\vis{\beta_j^{\in J\setminus \{j_0\}}} \quad  \text{ because $\Post_{1j}$  does not act on variables of $\beta_j$.}  
-\displaybreak[0]\\
-\Pred_c=&
-\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_{1i}}\land
-\left(Pred\land\Pred_2\land \alpha'_Q=\beta_{j_0}\right) \subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land\\
-&\bigwedge_{h=0}^{k'}{\Pred_{3h}}\subst{\bigotimes_{i=h-1}^{0}{\Post_{3i}}\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}
-\\
-\Post_c=&(\bigotimes_{i=k'}^{0}{\Post_{3i}})\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}
-\end{align*}
-\end{small}
-\noindent Note that we have $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$.
-
-Note also that $\Post$ only acts on variables of $P$ while $\Post_{1i}$ only acts on  variables of $Q$.
-We conclude on predicate and posts as follows\footnote{$\Post_{1i}$ only has an effect on variables of $Q$ and thus does not modify $\Pred$ or $\beta_{j_0}$}:
-\begin{equation*}
-\begin{split}
-\Pred_c&=\Pred_Q\land\Pred\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land
-(\alpha'_Q=\beta_{j_0})\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\\
-&=\Pred_Q\land\Pred\land \alpha_Q=\beta_{j_0}\\[.3ex]
-\Post_c&=\Post\uplus\Post_Q \qedhere
-\end{split}
-\end{equation*}
-\end{proof}
-\smallskip
-\begin{lemma}[Weak open transition composition]\label{lem-Weakcompose} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
-Suppose $j_0\in J$ and $\gamma_{j_0}=[\beta_0..\beta_n]$ and additionally:\\[-2ex]
-\begin{mathpar}
-%\[
-P\models{\openrule
-	{
-		\gamma_j^{j\in J}, 
-		\Pred,  
-		\Post}
-	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
-		\ostate{s_i'^{\, i\in L}}}
-}
-\qquad\text{~~and for all $p\in[0..n]$~~}\quad
-Q\models{\openrule
-	{
-		\gamma_{pj}^{j\in J_p},
-		 \Pred_p,  
-		\Post_p}
-	{\ostate{s_{pi}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
-		\ostate{s_{(p+1) i}^{\, i\in L_Q}}}
-}%\]
-\end{mathpar}
-
-Let 
-\begin{mathpar}
-J_Q=\displaystyle{\bigcup_{p=0}^nJ_{p}}
-
-\forall{i\in L_Q}.\,s_i=s_{0i}~~\land~~s'_i=s_{(n+1) i}
-
-\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}\subst{\bigotimes_{k=p}^{0}{\Post_k}}}
-
-\Pred\,'=\Pred\land \bigwedge_{p=0}^{n}(\alpha_p=\beta_p\land \Pred_p)\subst{\bigotimes_{i=p-1}^{0}\Post_i}
-
-\Post\,'=\Post\uplus\bigotimes_{p=n}^{0}
-		\Post_p
-\end{mathpar}
-Then, we have
-	\[ P[Q]_{j_0}  
-	\models
-	{\openrule
-		{
-			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
-			\Pred\,',  \Post\,'
-			 }
-		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
-			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
-	}
-	\]
-\end{lemma}
-
-\begin{proof} Suppose we have:
-\begin{mathpar}
-%\[
-P\models{\openrule
-	{
-		\gamma_j^{j\in J}, 
-		\Pred,  
-		\Post}
-	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
-		\ostate{s_i'^{\, i\in L}}}
-}
-\end{mathpar}
-By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
-%\begin{mathpar}
-\begin{small}
-$\forall p\!\in\![0\,..\,m_1].P\models\openrule
-    {{\beta_{1pj}^{j\in J_{1p}}},\Pred_{1p},\Post_{1p}   }
-         {\ostate{{(s_{1pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s_{1(p+1)i})}^{i\in L}}},  \quad
-P\models\openrule
-         {\beta_{2j}^{j\in J_2},\Pred_2,\Post_2 }
-         {\ostate{({s_{20i}})^{i\in L}} \OTarrow {\alpha'} \ostate{({s_{21i}})^{i\in L}}} $ 
-\\
-and  $\forall p \in [0\,..\,m_2].P\models\openrule
-         {
-           \beta_{3pj}^{j\in J_{3p}},\Pred_{3p}, \Post_{3p}}
-         { \ostate{(s_{3pi})^{i\in L}} \OTarrow {\tau} \ostate{(s_{3(p+1)i})^{i\in L}}}$
-\end{small}
-%\end{mathpar}
-
- where:
-{\small
-\begin{align*}
-\forall i\in L.&~~s_i=s_{10 i} \wedge s_{1(m_1+1) i}=s_{20i} \wedge  s_{21i}= s_{30 i} \wedge s_{3(m_2+1) i}=s'_i\\
-\alpha=&\alpha'{\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \\
-\gamma_j^{j\in J}=&{\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigotimes_{k=i-1}^{0}\!\!
-\Post_{1k} } }  \dotcup \, \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}}\, \dotcup\\
-&\mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{3p}} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}\\
-\Pred=&{\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\subst{\!\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}\big)\land\Pred_2\subst{\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\land}%\\ 
-%&
-{\bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\bigotimes_{j=p-1}^{0}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}}\\
-\Post=&{\bigotimes_{p=m_2}^{0}\Post_{3p}\otimes\Post_2\otimes\bigotimes_{j=m_1}^{0}\Post_{1j}}
-\end{align*}
-}
-
-Note that, for $l\in\{1,3\}$ if $\beta_{l p j_0}=\tau$, then, because of Definition \ref{def:Non-ObsTau}, $P$ necessarily makes a $\tau$ open transition and remains in the same state, e.g.
-$s_{1pi} = s_{1(p+1)i}$.
-Thus without loss of generality, we can bypass such an open transition and obtain another decomposition of the WOT without the open transition that requires ${\beta_{lp{j_0}}}=\tau$.
-We can thus  suppose that for all $p$ and $l$ we have ${\beta_{lp{j_0}}}\neq\tau$ or $j_0\not\in J_{1 p}$.
-To avoid a special case, we suppose that the hole $j_0$ moves during the OT $\alpha'$, i.e.
-$\beta_{2 j_0}=\beta_{m}$ for some $m$.
-Additionally, $\beta_{m}\neq \tau$, else we would have $\alpha=\alpha'=\tau$ and the $\alpha'$ OT could be also removed from the reduction, leading to a particular and simpler case.
-
-We introduce $n_i^{i\in[0..m-1]}$, and $(n'_i)^{i\in[m+1..n]}$ the indices of the steps in 
-which the hole $j_0$ moves in the 3 sets of OTs above ($\beta_m$ is the action that matches the hole $j_0$ in the OT $\alpha'$), in other words, we have for all $i$, $\beta_{1 n_i j_0}$ a visible action, as additionally:\\
-{\small
-\begin{align*}
-\gamma_{j_0}=&~[\beta_0..\beta_n]\\
- =&\!\!
-{\mybigdotcup_{\substack{i=0\\j_0\in J_{1i}}}^{m_1}\!\!\!
-\vis{{\beta_{1ij_0}}\subst{\!\bigotimes_{k=i-1}^{0} \!\!\!\Post_{1k} } }  \,\dotcup\, \vis{{\beta_{2j_0}}\subst{\!\bigotimes_{k=m_1}^{0}\!\!\Post_{1k}}}}\dotcup %\\
-%&
-{ \!\mybigdotcup_{\substack{i=0\\j_0\in J_{3i}}}^{m_2}\!\! \vis{{\beta_{3ij_0}} \subst{\!\bigotimes_{k=i-1}^{0}\!\!\!\Post_{3k}\shortotimes\Post_2\shortotimes
-\!\bigotimes_{k=m_1}^{0}\!\!\Post_{1k}}}}
-\end{align*}}
-
-\noindent We have, by definition of $n_i$ and $n'_i$:\\
-$\displaystyle{\forall{i\in[0\,..\,m\!-\!1]}, \beta_{1 n_i j_0}\subst{\bigotimes_{k=n_i-1}^{0}\Post_{1k}}=\beta_i}$, \qquad$\displaystyle{\beta_{2 j_0}\subst{\bigotimes_{k=m_1}^{0} \Post_{1k} }=\beta_m}$, and \\
-$\displaystyle{\forall{i\in[m\!+\!1\,..\,n]}, \beta_{3 n_i' j_0}\subst{\bigotimes_{k=n_i'-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}=\beta_i}$\\
-
-\noindent Now, we compose OTs for each of the case above (depending on the OT of $P$):
-\begin{enumerate}
-\item For the first $\tau$ OTs, i.e. $p\in [0\,..\,m_1]$. We have: \\
-Either there is $i$ such that $p=n_i$, and thus $\beta_i$ and $\beta_{1 p j_0}$ are defined. In this case by Lemma~\ref{lem-Weakcompose1},  we have: 
-\[ P[Q]_{j_0}  
-	\models
-	{\openrule
-		{
-			\set{\gamma'_{1p}}, 
-			\Pred\,'_{1p},  \Post\,'_{1p}
-			 }
-		{\ostate{s_{1pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTWeakarrow {\tau}
-			\ostate{s_{1(p+1)j}^{\, j\in L}\uplus s_{(i+1)j}^{j\in L_Q} } }
-	}
-	\]
-with 
-\begin{mathpar}
- \set{\gamma'_{1p}}=\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{1pj}^{j\in J_{1p}\setminus \{j_0\}}}
-
-\Pred\,'_{1p}=\Pred_{1p}\land (\beta_{1pj_0}=\alpha_i\land \Pred_i)
-
- \Post\,'_{1p}=\Post_{1p}\uplus\Post_i
-\end{mathpar}
-
-Or $j_0\not \in \dom(\beta_{1 p})$ and $Q$ does not move in the composed reduction. In this case there is no $i$ such that $p=n_i$, but there is $i$ such that $p\in]n_i .. n_{i+1}[$, and
-\[P[Q]_{j_0} \models\openrule
-    {\set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
-         {\ostate{s_{1pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTarrow {\tau} \ostate{s_{1(p+1)j}^{j\in L}\uplus s_{ij}^{j\in L_Q}}}
-\]
-and thus we also have a weak OT by Definition \ref{def:buildweakOT} (rule (\WTDeux)):
-\[P[Q]_{j_0} \models\openrule
-    {\set{\gamma'_{1p}},\Pred\,'_{1p},\Post\,'_{1p}   }
-         {\ostate{s_{1pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTWeakarrow {\tau} \ostate{s_{1(p+1)j}^{j\in L}\uplus s_{ij}^{j\in L_Q}}}
-\]
-with 
-$\set{\gamma'_{1p}}=\set{\vis{\beta_{1p}}}, \Pred\,'_{1p}=\Pred_{1p}, \Post\,'_{1p}=\Post_{1p}$\\
-
-\item Similarly, for the middle OT with label $\alpha$:
-\[P[Q]_{j_0}\models\openrule
-         {	\set{\gamma'_2},\Pred\,'_2,\Post\,'_2 }
-         {\ostate{{(s_{20j})}^{j\in L}\uplus (s_{mj})^{j\in L_Q}}\OTWeakarrow {\alpha'} \ostate{{(s_{21j})}^{j\in L}\uplus (s_{(m+1)j})^{j\in L_Q}}}\]
-with
-\begin{mathpar}
-\set{\gamma'_2}=\gamma_{m j}^{j\in J_m}\uplus\vis{\beta_{2j}^{j\in J_2\setminus \{j_0\}}}
-
-\Pred\,'_{2}=\Pred_{2}\land (\beta_{2j_0}=\alpha_m\land \Pred_m)
-
-\Post\,'_{2}=\Post_{2}\uplus\Post_m
-\end{mathpar}
-
-\item For the last $\tau$ OTs, i.e. $p\in [0\,..\,m_2]$. We have similarly to the first case:\\
- Either there is $i$ such that $p=n'_i$, and thus $\beta_i$ and $\beta_{1 p j_0}$ are defined. In this case by Lemma~\ref{lem-Weakcompose1}, we have: 
-	\[ P[Q]_{j_0}  
-	\models
-	{\openrule
-		{
-			\set{\gamma'_{3p}}, 
-			\Pred\,'_{3p} ,  \Post\,'_{3p} 
-			 }
-		{\ostate{s_{3pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTWeakarrow {\tau}
-			\ostate{s_{3(p+1)j}^{\, j\in L}\uplus s_{(i+1)j}^{j\in L_Q} } }
-	}
-	\]
-with
-\begin{mathpar}
-\set{\gamma'_{3p}}=\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{3pj}^{j\in J_{3p}\setminus \{j_0\}}}
-
-\Pred\,'_{3p}=\Pred_{3p}\land (\beta_{3pj_0}=\alpha_i\land \Pred_i)
-
-\Post\,'_{3p} =\Post_{3p}\uplus\Post_i
-\end{mathpar}
-
-Or $j_0\not \in \dom(\beta_{3 p})$ and $Q$ does not move in the composed reduction. In this case there is no $i$ such that $p=n'_i$, but there is $i$ such that $p\in]n'_i .. n'_{i+1}[$, and
-\[P[Q]_{j_0} \models\openrule
-    {\set{\beta_{3p}},\Pred_{3p},\Post_{3p}   }
-         {\ostate{s_{3pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTarrow {\tau} \ostate{s_{3(p+1)j}^{j\in L}\uplus s_{ij}^{j\in L_Q}}}
-\]
-and thus we also have a weak OT by definition \ref{def:buildweakOT} (rule \WTDeux):
-\[P[Q]_{j_0} \models\openrule
-    {\set{\gamma'_{3p}},\Pred\,'_{3p},\Post\,'_{3p}   }
-         {\ostate{s_{3pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTWeakarrow {\tau} \ostate{s_{3(p+1)j}^{j\in L}\uplus s_{ij}^{j\in L_Q}}}
-\]
-with 
-$\set{\gamma'_{3p}}=\set{\beta_{3p}}, \Pred\,'_{3p} =\Pred_{3p}, \Post\,'_{3p} =\Post_{3p}$
-\end{enumerate}
-
-\noindent By definition of weak open transition (Definition~\ref{def:buildweakOT}, rule \WTTrois),
- we obtain:
-
-	\[ P[Q]_{j_0}  
-	\models
-	{\openrule
-		{
-			\set{\gamma'}, 
-			\Pred\,'',  \Post\,''
-			 }
-		{\ostate{s_{10j}^{j\in L}\uplus s_{0j}^{j\in L_Q}} \OTWeakarrow {\alpha''}
-			\ostate{s_{3(m_2+1)j}^{\, j\in L}\uplus s_{(n+1)j}^{j\in L_Q} } }
-	}
-	\]
-Where
-{\small 
-\begin{align*}
-\alpha''=&\alpha'{\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}\\
-\set{\gamma'}=&
- \mybigdotcup_{i=0}^{m_1}\set{\gamma'_{1i}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{1k}}\,\dotcup\,
-\set{\gamma'_{2}}\subst{\bigotimes_{k=m_1}^{0}\Post\,'_{1k}}\,\dotcup
- \mybigdotcup_{i=0}^{m_2}\set{\gamma'_{3i}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}
-\displaybreak[0]\\
-\Pred\,''=&\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\ 
-&\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_2}^{0}\Post\,'_{1j}}\displaybreak[0]\\
-\Post\,''=&\bigotimes_{j=m_2}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}
-\end{align*}
-}
-
-However it must be noticed that in steps 1 and 3, we have two kinds of WOTs with different signatures (depending on whether $Q$ moves or not).
-It is still possible to glue them together in a global rule with two more terms for $\Pred$ and $\Post$ terms.
-This global merge is possible because the post-conditions of $P$ only act on variables of $P$ and those of $Q$ on variables of $Q$ (for example $\Post_i$ has no effect on $\Pred_{1p}$ and thus does not need to be taken into account when dealing with WOTs where $Q$ does not move).
-
-We now  compare each element of the obtained WOT with the conclusion of the lemma:
-{\small \begin{align*}
-\alpha''&=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}}\\
-& = \alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}}&\text{$\alpha'$ only contains variables of $P$ untouched by $\Post_i$}\\
-& = \alpha
-\end{align*}}
-
-For $\set{\gamma'}$ we distinguish elements in the holes of $P$ and of $Q$.
-
- First suppose $j\in J\setminus\{j_0\}$ we have $\gamma'_j=\gamma_j$ because $\Post^{\,\prime}_{ij}$ has no effect on variables of $P$ and on $\beta_{1pj}$, consequently\\
-{\small \begin{equation*}
-\begin{split}\gamma'_j=&\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}}\subst{\bigotimes_{k=i-1}^{0}\! \Post_{1k} } }  \dotcup  \vis{{\beta_{2j}}\subst{\bigotimes_{k=m_1}^{0}\!\Post_{1k}}}\, \dotcup
-\mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}
-\end{split}
-\end{equation*}
-}
-
-Second, when $j\in J_t$ for some $t$,  $\gamma'_j$ is the concatenation of elements of $\gamma'_{1ij}$, $\gamma'_{2 j}$, $\gamma'_{3ij}$  that are not empty.
-By construction the concatenation of these elements is $\gamma_{tj}$, for $t\in[0..n]$.
-$\Post_{ik}$ has no effect on $\gamma_{tj}$ but  $\Post_{k}$ has.
-%\TODO{do we want to be more explicit in the explanation?
-giving the exact indices is cumbersome because Post'ij is either empty or postij for the same indices as gamma, this can also be related with the ni and n'i}
-We obtain:
-{\small\begin{equation*}
-\begin{split}
-\gamma'_j =&
-\mybigdotcup_{i=0}^{m_1}{\gamma'_{1ij}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{1k}}\dotcup
- {\gamma'_{2 j}}\subst{\bigotimes_{k=m_1}^{0}\Post\,'_{1k}}\,\dotcup\, \mybigdotcup_{i=0}^{m_2}{\gamma'_{3ij}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}\\
-=&
-{\mybigdotcup_{t=0}^{n} {\gamma_{tj}}\subst{\bigotimes_{k=t-1}^{0} \Post_{k}}}   
-\end{split}
-\end{equation*}
-}
-
-Concerning predicates, we also separate predicates on $P$ from predicates on $Q$, and from the equality on the action filling the hole:
-%\begin{small}
-%\begin{equation*}
-%\begin{split}
-%\Pred\,''&=\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\
-%&~~{\bigwedge_{i=0}^{m_3}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}}\\
-%&=\big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\
-%&~~~\bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\big) \land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i \land
-%%$~\qquad\qquad\,\displaystyle{\bigwedge_{i=0}^{m-1}(\beta_{1{n_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j={n_i}-1}^{0}\Post\,'_{1j}}\land(\beta_{2{j_0}}=\alpha_m) \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land}
-%\end{split}
-%\end{equation*}
-%%$~\qquad\qquad\,\displaystyle{\bigwedge_{i=m+1}^{n}(\beta_{3{n'_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j=n'_i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\Big)}$\\
-%\end{small}
-\begin{footnotesize}
-\begin{align*}
-\Pred\,''&=\Big(\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land%\\ &\qquad
-%~\quad
-\bigwedge_{i=0}^{m_3}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\Post\,'_{1j}}\Big)\\
-&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}\land\Pred_2\subst{\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\Big)\\&\qquad
-\land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i%\\&\qquad
-\land \Big( \bigwedge_{i=0}^{m-1}(\beta_{1{n_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j={n_i}-1}^{0}\Post\,'_{1j}}\land(\beta_{2{j_0}}=\alpha_m) \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\ &\qquad
-~\quad\bigwedge_{i=m+1}^{n}(\beta_{3{n'_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j=n'_i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\Big)\displaybreak[0]\\
-&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}\big)\land\Pred_2\subst{\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\Big)\\&\qquad
-\land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i
-\land \Big(\bigwedge_{i=0}^{m-1}(\beta_{i}=\alpha_i)\subst{\bigotimes_{j={i-1}}^{0}\Post_{j}}\land(\beta_m=\alpha_m )\subst{\bigotimes_{j=m}^{0}\Post_{j}}\land\\ &\qquad
-~\quad\bigwedge_{i=m+1}^{n}(\beta_i=\alpha_i)\subst{\bigotimes_{j=i-1}^{m}\Post_j\shortotimes\Post_m\shortotimes\bigotimes_{j=m-1}^{0}\Post_{j}}\Big)\\
-&=\Pred
-\end{align*}
-\end{footnotesize}
-
-Finally, concerning post-conditions:
-{\footnotesize \begin{equation*}
-\begin{split}
-\Post\,''&=\bigotimes_{j=m_2}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}\\
-&=\left(\bigotimes_{j=m_2}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}\right)\uplus \bigotimes_{j=n}^{0}\Post_j\\
-&=\Post \uplus \bigotimes_{j=n}^{0}\Post_j\
-\end{split}
-\end{equation*}
-}
-This allows us to conclude concerning the lemma. 
-\end{proof}
-
-%\newpage
-
-%\begin
-\noindent
-{\bf Theorem~\ref{weak-thm-congr-eq}}. \emph{Congruence}.
-	Consider an open pNet:
-	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
-	\set{\symb{SV}}\myrangle$.
-	Let $j_0\in J$ be a hole. Let $\pNetQ$ and $\pNetQ'$ be two weak FH-bisimilar pNets such that 
-	$\Sortop(\pNetQ)=\Sortop(\pNetQ')=\Sort_{j_0}$. Then 
-	$\pNet[\pNetQ]_{j_0}$ and 
-	$\pNet[\pNetQ']_{j_0}$ are weak FH-bisimilar.
-%\end{theorem}
- \begin{proof}  Consider $Q$ weak FH-bisimilar to $Q'$.
-It means that there exist a FH-bisimulation $\mathcal{R}_{Q,Q'}$ relating the two pNets $Q$ and $Q'$.
-We define a relation $\mathcal{R}$ relating states of $P[Q]_{j_0}$ with states of $P[Q']_{j_0}$:
-\[\mathcal{R} = \{(\ostate{S_P\uplus S_Q},\ostate{S_P\uplus S_{Q'}}, \Pred_{Q,Q'})|\,(S_Q,S_{Q'}, \Pred_{Q,Q'})\in\mathcal{R}_{Q,Q'}\}\]
-
-To prove weak FH-bisimulation of $\pNet[\pNetQ]_{j_0}$ and 
-	$\pNet[\pNetQ']_{j_0}$, we consider  an open transition $OT$ of $\pNet[\pNetQ]_{j_0}$, and an equivalent state of $\pNet[\pNetQ']_{j_0}$, and we try to find a family of WOT of 	$\pNet[\pNetQ']_{j_0}$ that simulates $OT$.
-Consider an OT of  $\pNet[\pNetQ]_{j_0}$ it is of the form (notations introduced to prepare the decomposition):
-\[
-\pNet[\pNetQ]_{j_0}\models\openrule
-	{
-		\beta_j^{j\in( J_P\uplus J_Q)}, 
-		\Pred_P\land \Pred_Q,  
-		\Post_P\uplus \Post_Q}
-	{\ostate{S_P\uplus S_Q} \OTarrow {\alpha}
-		\ostate{S'_P\uplus S'_Q}
-}
-\]
-
-By the decomposition lemma for OTs (Lemma~\ref{lem-decompose}), we obtain the 2 following OTs (equality side-conditions have been inlined for clarity):
-\begin{mathpar}
-%\[
-\pNet\models{\openrule
-	{
-		\beta_j^{j\in J_P}\uplus(j_0\mapsto \alpha_Q), 
-		\Pred_P,  
-		\Post_Q}
-	{\ostate{S_P} \OTarrow {\alpha}
-		\ostate{S'_P}}
-}
-\quad\text{~~and~~}\quad
-Q\models{\openrule
-	{
-		\beta_j^{j\in J_Q},
-		 \Pred_Q,  
-		\Post_Q}
-	{\ostate{S_Q} \OTarrow {\alpha_Q}
-		\ostate{S'_Q}}
-}%\]
-
-\end{mathpar}
-
-By definition of $\mathcal{R}$ we have 
-$(S_Q,S_{Q'}| \Pred_{Q,Q'})\in\mathcal{R}_{Q,Q'}$. And thus, by definition of weak FH-bisimulation, there exist a family of weak open transitions $WOT_{x}$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j x}^{j\in J_Q}, \Pred_{Q' x},\Post_{Q' x}}
-         {\ostate{S_{Q'}}\OTWeakarrow {\alpha_{x}} \ostate{S'_{Q' x}}}
-\end{mathpar}
-
-where  
-\[\forall x.\, (S'_Q,S'_{Q' x}| \Pred_{Q,Q' x})\in\mathcal{R}_{Q,Q'}\]
-
-and
-{\small%\begin{equation*}
-\begin{multline*}
-\Pred_{Q,Q'}\land \Pred_Q \implies \\
-\bigvee_{x\in X}
-(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x})\Rightarrow (\Pred_{Q_x}\land%\\ %&~~
-\alpha_Q=\alpha_x \land \Pred_{Q,Q' x}\subst{\Post_{Q' x}\uplus \Post_{Q}}) 
-\end{multline*}
-%\end{equation*}
-}
-
-Composing the OT of $P$ with the WOTs of $Q'$ by Lemma~\ref{lem-Weakcompose1} we obtain:
-\[
-\pNet[\pNetQ']_{j_0}\models\openrule
-	{
-		\vis{\beta_j^{j\in J_P}}\uplus\gamma_{j x}^{j\in J_Q}, 
-		\Pred_P\land \Pred_{Q' x},  
-		\Post_P\uplus \Post_{Q' x}}
-	{\ostate{S_P\uplus S_{Q'}} \OTWeakarrow {\alpha}
-		\ostate{S'_P\uplus S'_{Q' x}}
-}
-\]
-with $\displaystyle{\bigvee_{x\in X}
-\big(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x} \implies \alpha_Q=\alpha_x\big)}$ that ensures that the open transitions can be recomposed when the OT fires.
-
-Side conditions necessary to prove weak-FH bisimulations are:
-\[\forall x.\, (S'_P\uplus S'_Q,S'_P\uplus S'_{Q' x}| \Pred_{Q,Q' x})\in\mathcal{R}\]
-which is true, and
-\begin{multline*}
-\Pred_{Q,Q'}\land \Pred_P\land \Pred_Q \implies \\
-\Big(\bigvee_{x\in X}
-(\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x}\land \forall j\in J_P.\, \vis{\beta_j}=\vis{\beta_j}))\Rightarrow \\(\Pred_P\land \Pred_{Q' x}\land \alpha=\alpha \land \Pred_{Q,Q' x}\subst{\Post_P\uplus\Post_{Q' x}\uplus \Post_{Q}}) \Big)
-\end{multline*}
-We conclude by observing that $\Post_P$ has no effect on variables of $Q$ and $Q'$, and thus on $\Pred_{Q,Q' x}$
-% OLD
-% according to Lemma  \ref{lem-alternative-weak-bisim} for any weak open transition $WOT$ in $Q$ there exist a family of weak open transitions $WOT_{x}^{x \in X}$ in $Q'$. 
-%We apply  Lemma \ref{lem-Weakcompose1} on weak open transition $WOT$, $j_0 \in J$, we obtain a new weak open transition $WOT'$ in $P[Q]_{j_0}$.
-%On other hand, we apply same Lemma \ref{lem-Weakcompose1} on each weak open transitions $WOT_{x}$, so we obtain a new family of weak open transitions $WOT_{x}'$ in $P[Q']_{j_0}$.
-%
-%Suppose we have:\\[-2ex]
-%\begin{mathpar}
-%%\[
-%P\models{\openrule
-%	{
-%		\beta_j^{j\in J}, 
-%		\Pred,  
-%		\Post}
-%	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
-%		\ostate{(s_i')^{\, i\in L}}}
-%}
-%\quad\text{~~and~~}\quad
-%Q\models{\openrule
-%	{
-%		\set{\gamma},
-%		 \Pred_Q,  
-%		\Post_Q}
-%	{\ostate{s_{i}^{i\in L_Q}} \OTWeakarrow {\alpha_Q}
-%		\ostate{(s'_{i})^{\, i\in L_Q}}}
-%}%\]
-%
-%
-%\end{mathpar}
-%
-%Then, we have by lemma \ref{lem-Weakcompose}: \\[-2ex]
-%	\[ P[Q]_{j_0}  
-%	\models
-%	{\openrule
-%		{
-%			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
-%			\Pred\,',  \Post\,'
-%			 }
-%		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
-%			\ostate{(s_i')^{\, i\in L\uplus L_Q}}}
-%	}
-%	\]
-%
-%On the other hand, $Q$ weak FH-bisimilar to $Q'$, so according to  Lemma  \ref{lem-alternative-weak-bisim} 
-%
-%such that...\\
-%
-%By applying  Lemma \ref{lem-Weakcompose} on each weak open transitions $WOT_{x}$, so we obtain a new family of weak open transitions $WOT_{x}'$ in $P[Q']_{j_0}$:
-%
-%\[ P[Q']_{j_0}  
-%	\models
-%	{\openrule
-%		{
-%			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
-%			\Pred\,',  \Post\,'
-%			 }
-%		{\ostate{s_i^{i\in L} \uplus t_{i}^{i\in L_{Q_x}}} \OTWeakarrow {\alpha}
-%			\ostate{(s_i')^{\, i\in L} \uplus t_{ix}^{i\in L_{Q_x}} }}
-%	}
-%	\]
- \end{proof}
-
-\noindent {\bf Theorem~\ref{weak-thm-ctxt-eq}}. \emph{Context equivalence}.
-	Consider two FH-bisimilar open pNets:\\
-	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
-	\set{\symb{SV}}\myrangle$ and 	$\pNet' = \mylangle {\pNet'}_i^{i\in I}, 
-	\Sort_j^{j\in 
-	J}, 	\set{\symb{SV'}}\myrangle$ 
-	(recall they must have the same holes to be bisimilar).
-	Let $j_0\in J$ be a hole, and $Q$ be a pNet such that $\Sortop(Q)=\Sort_{j_0}$. Then 
-	$\pNet[Q]_{j_0}$ and 
-	$\pNet'[Q]_{j_0}$ are FH-bisimilar.
-%\end{theorem}
-
- \begin{proof}   Consider $P$ weak FH-bisimilar to $P'$.
-There exist a FH-bisimulation $\mathcal{R}_{P,P'}$ relating $P$ and $P'$.
-We define a relation $\mathcal{R}$ relating states of $P[Q]_{j_0}$ with states of $P'[Q]_{j_0}$:
-\[\mathcal{R} = \{(\ostate{S_P\uplus S_Q},\ostate{S_{P'}\uplus S_Q}, \Pred_{P,P'})|\,(S_P,S_{P'}, \Pred_{P,P'})\in\mathcal{R}_{P,P'}\}\]
-
-To prove weak FH-bisimulation of $\pNet[\pNetQ]_{j_0}$ and 
-	$\pNet'[\pNetQ]_{j_0}$, we consider  an open transition $OT$ of $\pNet[\pNetQ]_{j_0}$, and an equivalent state of $\pNet'[\pNetQ]_{j_0}$, and we try to find a family of WOT of 	$\pNet'[\pNetQ]_{j_0}$ that simulates $OT$.
-Consider an OT of  $\pNet[\pNetQ]_{j_0}$ it is of the form (notations introduced to prepare the decomposition):
-\[
-\pNet[\pNetQ]_{j_0}\models\openrule
-	{
-		\beta_j^{j\in( J_P\uplus J_Q)}, 
-		\Pred_P\land \Pred_Q \land \Pred,  
-		\Post_P\uplus \Post_Q}
-	{\ostate{S_P\uplus S_Q} \OTarrow {\alpha}
-		\ostate{S'_P\uplus S'_Q}
-}
-\]
-
-By the decomposition lemma for OTs (Lemma~\ref{lem-decompose}), we obtain the 2 following OTs (equality side-conditions have been inlined for clarity):
-\begin{mathpar}
-%\[
-\pNet\models{\openrule
-	{
-		\beta_j^{j\in J_P}\uplus(j_0\mapsto \alpha_Q), 
-		\Pred_P,  
-		\Post_Q}
-	{\ostate{S_P} \OTarrow {\alpha}
-		\ostate{S'_P}}
-}
-\quad\text{~~and~~}\quad
-Q\models{\openrule
-	{
-		\beta_j^{j\in J_Q},
-		 \Pred_Q,  
-		\Post_Q}
-	{\ostate{S_Q} \OTarrow {\alpha_Q}
-		\ostate{S'_Q}}
-}%\]
-
-\end{mathpar}
-
-With $\Pred \iff \alpha_Q=\beta_{j_0}$
-
-By definition of $\mathcal{R}$ we have 
-$(S_P,S_{P'}, \Pred_{P,P'})\in\mathcal{R}_{P,P'}$. And thus, by definition of weak FH-bisimulation, there exist a family of weak open transitions $WOT_{x}$:
- \begin{mathpar}
-    \openrule
-         {
-           \gamma_{j x}^{j\in J_P\uplus\{j_0\}}, \Pred_{P' x},\Post_{P' x}}
-         {\ostate{S_{P'}}\OTWeakarrow {\alpha_{x}} \ostate{S'_{P' x}}}
-\end{mathpar}
-
-where  
-\[\forall x.\, (S'_P,S'_{P' x}, \Pred_{P,P' x})\in\mathcal{R}_{P,P'}\]
-and
-\begin{equation*}
-\begin{split}
-\Pred_{P,P'}\land \Pred_P \implies &
-\Big(\bigvee_{x\in X}
-(\forall j\in J_P.\, \vis{\beta_j}=\gamma_{j x} \land \vis{\alpha_Q}=\gamma_{j_0})\Rightarrow (\Pred_{P'_x}\land\\ &~~\alpha=\alpha_x \land \Pred_{P,P' x}\subst{\Post_{P' x}\uplus \Post_{P}}) \Big)
-\end{split}
-\end{equation*}
-
-We here need a special case of Lemma~\ref{lem-Weakcompose} where the inner pNet $Q$ does a simple OT.
-This is just a particular case of the theorem but where notations get simplified because the inner pnet does a single transition.
- This way we can compose the WOTs of $P'$ with the OT of $Q$ and obtain, with $\gamma_{j_0}=[\beta] $:
-\[
-\pNet'[\pNetQ]_{j_0}\models\openrule
-	{
-		\vis{\beta_j^{j\in J_Q}}\uplus\gamma_{j x}^{j\in J_P}, 
-		\Pred_{P' x}\land \Pred_Q \land \alpha_Q=\beta,  
-		\Post_{P' x}\uplus \Post_Q}
-	{\ostate{S_{P'}\uplus S_{Q}} \OTWeakarrow {\alpha_x}
-		\ostate{{S'_{P' x}}\uplus S'_Q}
-}
-\]
-Side conditions necessary to prove weak-FH bisimulations are:
-\[\forall x.\, (S'_P\uplus S'_Q,S'_{P' x}\uplus S'_Q, \Pred_{P,P' x})\in\mathcal{R}\]
-which is true, and
-\begin{multline*}
-\Pred_{P,P'}\land \Pred_P\land \Pred_Q \Pred \implies \\
-\Big(\bigvee_{x\in X}
-(\forall j\in J_P.\, \vis{\beta_j}=\gamma_{j x} \land \forall j\in J_Q.\, \vis{\beta_j}=\vis{\beta_j} )\Rightarrow\\
- (\Pred_{P' x}\land \Pred_Q\land \alpha_Q=\beta\land  \alpha_x=\alpha \land \Pred_{P,P' x}\subst{\Post_{P' x}\uplus\Post_P\uplus \Post_{Q}}) \Big)
-\end{multline*}
-We conclude by observing that $\Post_Q$ has no effect on variables of $P$ and $P'$, and thus on $\Pred_{P,P' x}$ and $\Pred$ leading to the conclusion about $\alpha_Q=\beta$.
-\end{proof}
-
-\newpage
-
-\section{Full details of the Simple Protocol Example}
-
-\label{Appendix:FullExample}
-
-%% \begin{figure}[t]
-%%    \includegraphics[width=5.5cm]{XFIG/SimpleProt-Schema}
-%%    \includegraphics[width=6.5cm]{XFIG/SimpleProt2-Spec}
-%%    \caption{Specification pNet Schema and Specification}
-%%    \label{App:SimpleProt:Spec}
-
-%% \end{figure}
-
-%% \begin{figure}[t]
-%%   \centerline{\includegraphics[width=12cm]{XFIG/SimpleProt2-pNet}}
-%%   \caption{Composed pNet with the Simple Protocol Implementation}  \label{App:SimpleProt:Impl}
-%% \end{figure}
-
-The first piece of code is the textual definition of the SimpleProtSpec
-pNet, that was drawn in Figure \ref{SimpleProt:Impl}, page \pageref{SimpleProt:Impl}. This code should be intuitive enough to read, with the following
-conventions, that brings some user-friendly features that are mapped by the editor into pure pNet constructs.
-
-\begin{itemize}
-  \item Constants of any type (including Action) must be declared as
-    ``const''. They are used either as functions with argument, as
-    typically \texttt{in(msg)}, or constants without argument, denoted
-    as \texttt{\$tau}. Identifiers without the ``\$'' marker are
-    variables.
-  \item Variables can be declared as global variables of a pLTS (e.g. \texttt{m\_msg} in \texttt{M1}), or a pNet Node in the case of synchronisation vector variables (e.g. \texttt{p\_a}),
-    or as input variables in a pLTS, as \texttt{?msg} in \texttt{M1}.
-  \item The variables in the guards of synchronisation vectors do not need to be explicitly quantified: by convention, all variables in a guard that do not appear inside the vector actions will be recognised as bound by a \emph{forall} quantifier inside the guard.
-    \item The tools will check that everything is correctly declared, and that variables are used properly and do not conflict between different objects, that vectors have coherent length, etc.
-\end{itemize}
-\bigskip
-%\TODO{Je ne peux pas refaire tourner le code, il faut que je modifie le pNet Editor pour qu'ils n'utilise plus les variables d'etat... Donc les 3 prochaines pages sont obsoletes...}
-%% \TODO{keep ?}
-%% \paragraph{Variable management.}
-%% The variables in each synchronisation vector are considered local:
-%% for a given pNet expression, we must have fresh local variables for
-%% each occurrence of a vector (i.e. each time we instantiate rule
-%% \TrDeux). Similarly the state variables of each copy of a
-%% given pLTS in the system, must be distinct, and those created for each
-%% application of \TrDeux\ have to be fresh and all distinct. 
-%% This is implemented within the open-automaton generation algorithm,
-%% using name generation using a global counter as a suffix.
-
-\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
-SimpleProtSpec2:
-import "Data_Alg.algp"
-root SimpleProtSpec2
-const in, out:Action
-const p_send, q_recv: Action
-const tau:Action
-
-pLTS M1
-initial a0 
-vars ?msg:Data
-vars m_msg:Data m_ec:Int
-
-state a0
-transition in(msg) -> a1 {m_msg:=msg, m_ec:=0}
-
-state a1
-transition out(m_msg, m_ec) -> a0
-transition synchro($tau)  -> a1 {m_ec:=m_ec+1}
-
-pNet SimpleProtSpec2
-holes P,Q
-subnets P,M1,Q
-vars p_a,q_a:Action m:Data ec:Int
-
-vector SV0 <p_send(m), in(m),_>->synchro(in(m))
-vector SV1 <p_a,_,_>->p_a [p_a != p_send(m)]
-vector SV2 <_, out(m,ec), q_recv(m)>->synchro(out(m,ec))
-vector SV3 <_,_,q_a>->q_a [q_a != q_recv(m)]
-
-  \end{lstlisting}
-
-\bigskip
-The corresponding generated Open Automaton was given in Figure \ref{SimpleProtCounter:SpecOA},
-page \pageref{SimpleProtCounter:SpecOA}.\\
-
-Next is the code for the SimpleProtImpl pNet:
-\medskip
-\begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
-SimpleProtImpl2:
-  import "Data_Alg.algp"
-  root SimpleProtImpl2
-const in,out:Action
-const tau,p_send,q_recv,m_recv,m_send,m_error: Action
-const s_recv,s_send,s_ack,s_error,r_recv,r_ack,r_send: Action
-
-pLTS M1
-  initial a0
-  vars ?msg:Data ?c:Int
-  vars m_msg:Data m_ec:Int
-state m0
-  transition m_recv(msg,c) -> m1 {m_msg:=msg, m_ec:=c}
-state m1
-  transition m_send(m_msg, m_ec) -> m0 
-  transition synchro($tau) -> m2
-state m2
-  transition $m_error -> m0
-
-pLTS Sender
-  initial s0
-  vars ?msg:Data
-  vars  s_msg:Data s_ec:Int
-state s0
-  transition s_recv(msg) -> s1 {s_msg:=msg, s_ec:=0}
-state s1
-  transition s_send(s_msg, s_ec) -> s2 
-state s2
-  transition $s_ack -> s0
-  transition $s_error -> s1 {s_ec:=s_ec+1}
-
-pLTS Receiver
-  initial r0
-  vars ?msg:Data ?c:Int
-  vars r_msg:Data r_ec:Int
-state r0
-  transition r_recv(msg,c) -> r1 {r_msg:=msg, r_ec:=c}
-state r1
-  transition r_send(r_msg, r_ec) -> r2
-state r2
-  transition $r_ack -> r0
-
-pNet medium
-  subnets Sender, M1, Receiver
-  vars m:Data c:Int
-vector SV0 <s_recv(m), _, _>->in(m)
-vector SV1 <s_send(m,c), m_recv(m,c), _>->synchro($tau)
-vector SV2 <_, m_send(m,c), r_recv(m,c)>->synchro($tau)
-vector SV3 <$s_ack, _, $r_ack>->synchro($tau)
-vector SV4 <$s_error, $m_error, _>->synchro($tau)
-vector SV5 <_, _, r_send(m,c)>->out(m,c)
-
-pNet SimpleProtImpl2
-  holes P,Q
-  subnets P,medium,Q
-  vars p_a,q_a:Action  m:Data c:Int
-vector SV0 <p_send(m), in(m),_>->synchro(in(m))
-vector SV1 <p_a,_,_>->p_a [p_a != p_send(m)]
-vector SV2 <_, out(m,c), q_recv(m,c)>->synchro(out(m,c))
-vector SV3 <_,_,q_a>->q_a [q_a != q_recv(m,c)]
-\end{lstlisting}
-
-%% From this code,A more compact view (maybe more readable ???) is given
-%% by the pretty-printer of VerCors:
-
-%% \begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
-%% SimpleProtImpl2
-%% --------------------
-%% SV6 SVs: <p_send(m), in(m), _>-->in(m)
-%% SV7 SVs: <p_a, _, _>-->p_a, p_a!=(p_send(m))
-%% SV8 SVs: <_, out(m, c), q_recv(m, c)>-->out(m, c)
-%% SV9 SVs: <_, _, q_a>-->q_a, q_a!=(q_recv(m, c))
-%% SV11 SVs: <_, _tau_, _>-->_tau_
-%% Holes: P
-%% Subnets: medium
-%% - medium
-%% - SV0 SVs: <in(m), _, _>-->in(m)
-%% - SV1 SVs: <s_send(m, c), m_recv(m, c), _>-->_tau_
-%% - SV2 SVs: <_, m_send(m), r_recv(m)>-->_tau_
-%% - SV3 SVs: <s_ack, _, r_ack>-->_tau_
-%% - SV4 SVs: <s_error, m_error, _>-->_tau_
-%% - SV5 SVs: <_, _, out(m, c)>-->out(m, c)
-%% - SV10 SVs: <_, _tau_, _>-->_tau_
-%% - pLTS: Sender
-%% - - Transition: s0---in(msg)-->s1, { s1_msg := msg s1_ec := 0}
-%% - - Transition: s1---s_send(s1_msg, s1_ec)-->s2, {}
-%% - - Transition: s2---s_ack-->s0, {}
-%% - - Transition: s2---s_error-->s1, { s1_ec := s2_ec+1}
-%% - - Variable: s1_ec, State: s1, Value(s) = 0,s2_ec+1,
-%% - - Variable: s1_msg, State: s1, Value(s) = msg,
-%% - pLTS: M1
-%% - - Transition: a0---m_recv(msg, c)-->a1, { a1_msg := msg a1_ec := c}
-%% - - Transition: a1---m_send(a1_msg, a1_ec)-->a0, {}
-%% - - Transition: a1---_tau_-->a2, {}
-%% - - Transition: a2---m_error-->a0, {}
-%% - - Variable: a1_msg, State: a1, Value(s) = msg,
-%% - - Variable: a1_ec, State: a1, Value(s) = c,
-%% - pLTS: Receiver
-%% - - Transition: r0---r_recv(msg, c)-->r1, { r1_msg := msg r1_ec := c}
-%% - - Transition: r1---out(r1_msg, r1_ec)-->r2, {}
-%% - - Transition: r2---r_ack-->r0, {}
-%% - - Variable: r1_msg, State: r1, Value(s) = msg,
-%% - - Variable: r1_ec, State: r1, Value(s) = c,
-%% Holes: Q
-%% \end{lstlisting}
-
-%% And here is a  drawing of this open automaton, slightly simplified for readability:
-
-%% \begin{figure}[h]
-%%   \centerline{\includegraphics[width=10cm]{ATG/SPImplOpen}}
-%%   \caption{Open Automaton of the Simple Protocol Implementation}  \label{Annex:SimpleProtCounter:ImplOA}
-%% \end{figure}
-
-%% And a partially saturated Automaton:
-
-%% \begin{figure}[h]
-%%   \centerline{\includegraphics[width=13cm]{ATG/SPImplWeakOpen}}
-%%   \caption{Weak Open Automaton, partial}  \label{SimpleProtCounter:ImplWOA}
-%% \end{figure}
-
-%% In Figure \ref{Annex:SimpleProtCounter:ImplWOA}, we have added some of the weak transitions generated by the saturation, namely:
-%% - a tau-loop on each state
-%% - a transition from <s0\_a0\_r0> to <s\_a\_r0>, resulting from the sequence OT\-1;OT\-6 followed by any number of the loop (OT\_9;ot\_12;OT\_6).
-%%
-%%Many weak should be added, e.g. Tau loops on states <s\_a\_r0>, <s\_a\_r0>, 
-%%<s\_a0\_r0>, encoding the loop.
-
-\begin{figure}[h]
-   \centerline{\includegraphics[width=10cm]{XFIG/SimpleProtImpl-WOA2}}
-   \caption{Weak Open Automaton of the implementation}
-   \label{Appendix:ImplOA2}
- \end{figure}
-
-In Figure \ref{Appendix:ImplOA2} we recall the weak open automaton of our implementation pNet.
-
-This drawing is based on the observation that states 202 and 000 are only linked by a "pure $\tau$" transition, and have exactly the same possible behaviours.
-%More tricky, they do not have the same state variables, as 202 has the variables of state $s2$, but none of these variables are used in transitions from 202.
-In this configuration we can guarantee that they are Weak bisimilar, and we have merged their (incoming and outgoing) transitions in the Figure. We denote this 
-equivalence class of states as $\{000,202\}$.
-
-% \TODO{May be express this property more formerly, but this could be also part of another paper, more oriented towards algorithms and optimisation of the Weak}
-
-Full details of the weak transitions is listed here:
-
-In the first 3 weak transitions, $S$ denotes the set of all global states.
-
-$ W_\tau = \openrule
-{\{\}, True, ()}
-{S \OTWeakarrow {\tau} S}$
-
-$ WI_1 = \openrule
-{\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{x}. \texttt{p-a} \neq \texttt{p-send(x)} ], ()}
-{S \OTWeakarrow {\texttt{p-a}} S}$
-
-$ WI_2 = \openrule
-{\{\texttt{Q}\mapsto \texttt{q-b}\}, [\forall \texttt{x,y}. \texttt{q-b} \neq \texttt{q-recv(x,y)} ], ()}
-{S \OTWeakarrow {\texttt{q-b}} S}$
-
-All the following transitions are parametrized by an integer $n\in \mathcal{N}$, meaning they stand for the corresponding (infinite) set of weak OTs. 
-In some cases, this set is further restricted (see e.g. $WI_{7b}(n)$), in which cases we have added an explicit quantifier.
-\smallskip
-
-$ WI_3(n) = \openrule
-  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
-    (\texttt{s\_msg}\gets \texttt{m}, \texttt{s\_ec}\gets n)}
-  { \{000,202\} \OTWeakarrow {\nounderline{\texttt{in(m)}}} 100}
-$
-
-$ WI_{3a}(n) = \openrule
-  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
-    (\texttt{m\_msg}\gets \texttt{m}, \texttt{m\_ec}\gets n, \texttt{s\_ec}\gets n)}
-  { \{000,202\} \OTWeakarrow {\nounderline{\texttt{in(m)}}} 210}
-$
-
-$ WI_{3b}(n) = \openrule
-  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
-    (\texttt{s\_ec}\gets n)}
-  { \{000,202\} \OTWeakarrow {\nounderline{\texttt{in(m)}}} 220}
-$
-
-$ WI_{3c}(n) = \openrule
-  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
-    (\texttt{r\_msg}\gets \texttt{m}, \texttt{r\_ec}\gets n)}
-  { \{000,202\} \OTWeakarrow {\nounderline{\texttt{in(m)}}} 201}
-$
-
-$ WI_4(n) = \openrule
-         {\{\}, True, 
-   (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec}+n, \texttt{s\_ec}\gets \texttt{s\_ec}+n)}
-         {100 \OTWeakarrow {\tau} 210}
-$
-
-$ WI_{4a}(n) = \openrule
-         {\{\}, True, 
-    (\texttt{s\_ec}\gets \texttt{s\_ec}+n)}
-         {100 \OTWeakarrow {\tau} 220}
-$
-
-$ WI_5(n) = \openrule
-         {\{\}, True, (\texttt{s\_ec}\gets \texttt{s\_ec}+n)}
-         {210 \OTWeakarrow {\tau} 220}
-         $
-
-$ WI_{5a}(n) = \openrule
-         {\{\}, True, (\texttt{s\_ec}\gets \texttt{s\_ec}+1+n)}
-         {210 \OTWeakarrow {\tau} 100}
-         $
-
-$ WI_6(n) = \openrule
-         {\{\}, True, (\texttt{s\_ec}\gets \texttt{s\_ec}+1+n)}
-         {220 \OTWeakarrow {\tau} 100}
-         $
-
-$ WI_{6a}(n) = \openrule
-         {\{\}, True, 
-         (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec}+1+n, \texttt{s\_ec}\gets \texttt{s\_ec}+1+n)}
-         {220 \OTWeakarrow {\tau} 210}
-         $
-
-Because 
-\begin{align*}
-Post_{6a}&=\ post_{4}\shortotimes\ post_{456}^*\shortotimes\ post_{6}\\
-&= \left( (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec})
-\shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+n) \right)
-\shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+1) \\
-&= (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets (\texttt{s\_ec}+1)+n, \texttt{s\_ec}\gets (\texttt{s\_ec}+1)+n)
-\end{align*}
-
-$ WI_{456*}(n) = \openrule
-         {\{\}, True, 
-    (\texttt{s\_ec}\gets \texttt{s\_ec}+n)}
-  {100 \OTWeakarrow {\tau} 100}
-        $
-
-$ WI_{564*}(n) = \openrule
-         {\{\}, True, 
-    (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{s\_ec}\gets \texttt{s\_ec}+1+n, \texttt{m\_ec}\gets \texttt{s\_ec}+1+n)}
-  {210 \OTWeakarrow {\tau} 210}
-        $
-
-$ WI_{645*}(n) = \openrule
-         {\{\}, True, 
-    (\texttt{s\_ec}\gets \texttt{s\_ec}+1+n)}
-  {220 \OTWeakarrow {\tau} 220}
-        $
-
-\medskip
-$ WI_7(n) = \openrule
-         {\{\}, True, (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_ec}+n)}
-         {210 \OTWeakarrow {\tau} 201}
-         $
-
-$ WI_{7a}(n) = \openrule
-         {\{\}, True, (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{m\_ec}+n)}
-         {220 \OTWeakarrow {\tau} 201}
-         $
-
-$ \forall n\ge 1. WI_{7b}(n) = \openrule
-         {\{\}, True, (\texttt{r\_msg}\gets \texttt{m\_msg}, \texttt{r\_ec}\gets \texttt{s\_ec}+n)}
-         {100 \OTWeakarrow {\tau} 201}
-         $
-
-$ WI_8 = \openrule
-         {\{\texttt{Q}\mapsto \texttt{q-recv(r1-msg,r1-ec)}\}, True, ()}
-         {201 \OTWeakarrow {\nounderline{\texttt{out(r1-msg,r1-ec)}}} \{202, 000\}}
-         $
-
-$ \forall n\ge 1. WI_{8a}(n) = \openrule
-         {\{\texttt{Q}\mapsto \texttt{q-recv(m\_msg,m\_ec}+n)\}, True, ()}
-         {210 \OTWeakarrow {\nounderline{\texttt{out(m\_msg,m\_ec}+n)}} \{202, 000\}}
-         $
-
- $ \forall n\ge 1.  WI_{8b}(n) = \openrule
-         {\{\texttt{Q}\mapsto \texttt{q-recv(??\_msg,s\_ec}+n)\}, True, ()}
-         {220 \OTWeakarrow {\nounderline{\texttt{out(??\_msg,m\_ec}+n)}} \{202, 000\}}
-         $
-
- $ \forall n\ge 1.  WI_{8c}(n) = \openrule
-         {\{\texttt{Q}\mapsto \texttt{q-recv(s\_msg,s\_ec}+n)\}, True, ()}
-         {100 \OTWeakarrow {\nounderline{\texttt{out(s\_msg,s\_ec}+n)}} \{202, 000\}}
-         $
-
-\medskip
-Then for all $\tau$ transitions above we have a similar WOT that include a non-$\tau$ move from an external action of P or Q, like for example:
-
-$ WI_4P(n) = \openrule
-         {\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{x}. \texttt{p-a} \neq \texttt{p-send(x)} ], \\
-   (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec}+n, \texttt{s\_ec}\gets \texttt{s\_ec}+n)}
-         {100 \OTWeakarrow {\texttt{p-a}} 210}
-$
-
-and
-$ WI_4Q(n) = \openrule
-         {\{\texttt{Q}\mapsto \texttt{q-b}\}, [\forall \texttt{x,y}. \texttt{q-b} \neq \texttt{q-recv(x,y)} ],\\
-   (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec}+n, \texttt{s\_ec}\gets \texttt{s\_ec}+n)}
-         {100 \OTWeakarrow {\texttt{q-b}} 210}
-$
-
-but also e.g.:
-
-$ WI_{456*}P(n) = \openrule
-        {\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{x}. \texttt{p-a} \neq \texttt{p-send(x)} ], 
-    (\texttt{s\_msg}\gets \texttt{s\_msg}, \texttt{s\_ec}\gets \texttt{s\_ec}+n)}
-  {100 \OTWeakarrow {\texttt{p-a}} 100}
-        $
-
-\bigskip
-The following table give a summary of  WOTs, when sharing their names as much as possible.
-
-\begin{tabular}{|l|l|c|}
-\hline
-    WOT name & Pairs of source states and target states & \# of WOTs \\
-    \hline
-    $WI_1$ $WI_2$ $WI_\tau$ & $\{(s,s)| s \in \texttt{States of WOA}\} \cup \{(202,000)\} $ & 21 \\
-    $WI_3(n)$ & \{(202,100),(000,100)\} & 2 \\
-    $WI_{3a}(n)$ & \{(202,210),(000,210)\} & 2 \\
-    $WI_{3b}(n)$ & \{(202,220),(000,220)\} & 2 \\
-    $WI_{3c}(n)$ & \{(202,201),(000,201)\} & 2 \\
-    $WI_4(n)$ $WI_4P(n)$ $WI_4Q(n)$ & \{(100,210)\} & 3 \\
-    $WI_{4a}(n)$ $WI_4aP(n)$ $WI_4aQ(n)$ & \{(100,220)\} & 3 \\
-    $WI_{456*}(n) $ $WI_{456*}P(n) $ $WI_{456*}Q(n) $ & \{(100,100)\} & 3 \\
-    $WI_5(n)$ $WI_5P(n)$ $WI_5Q(n)$ & \{(210,220)\} & 3 \\
-    $WI_{5a}(n)$ $WI_{5a}P(n)$ $WI_{5a}Q(n)$ & \{(210,100)\} & 3 \\
-    $WI_{564*}(n) $ $WI_{564*}P(n) $ $WI_{564*}Q(n) $ & \{(210,210)\} & 3 \\
-    $WI_6(n)$ $WI_6P(n)$ $WI_6Q(n)$ & \{(220,100)\} & 3 \\
-    $WI_{6a}(n)$ $WI_{6a}P(n)$ $WI_{6a}Q(n)$ & \{(220,210)\} & 3 \\
-    $WI_{645*}(n) $ $WI_{645*}P(n) $ $WI_{645*}Q(n) $ & \{(220,220)\} & 3 \\
-    $WI_7(n)$ $WI_7P(n)$ $WI_7Q(n)$ & \{(210,201)\} & 3 \\
-    $WI_{7a}(n)$ $WI_{7a}P(n)$ $WI_{7a}Q(n)$ & \{(220,201)\} & 3 \\
-    $WI_{7b}(n)$ $WI_{7b}P(n)P$ $WI_{7b}Q(n)$ & \{(100,201)\} & 3 \\
-    $WI_8(n)$ & \{(201,202),(201,000)\} & 2\\ 
-    $WI_{8a}(n)$ & \{(210,202),(210,000)\} & 2 \\
-    $WI_{8b}(n)$ & \{(220,202),(220,000)\} & 2 \\
-    $WI_{8c}(n)$ & \{(100,202),(100,000)\} & 2 \\
-
-    \hline
-    \end{tabular}
-
-    \bigskip
-    That makes a total of 73 WOTs  in the SimpleImpl WOA.
-
-        \subsection{Details of the Bisimulation Checking}
-
-We recall here the relation $\mathcal{R}$ that is the candidate for our weak bisimulation relation:
-
-\bigskip
-  \begin{tabular}{|c|c|l|}
-\hline
-    Spec state & Impl state & Predicate\\
-    \hline
-    b0 & $000$ & True\\
-    b0 & $202$ & True\\
-    b1 & $100$ & $\texttt{b\_msg = s\_msg} \land \texttt{b\_ec = s\_ec}$\\
-    b1 & $210$ & $\texttt{b\_msg = m\_msg} \land \texttt{b\_ec = m\_ec}$\\
-    b1 & $220$ & $\texttt{b\_msg = s\_msg} \land \texttt{b\_ec = s\_ec}$\\
-    b1 & $201$ & $\texttt{b\_msg = r\_msg} \land \texttt{b\_ec = r\_ec}$\\
-    \hline
-    \end{tabular}
-
-\bigskip
-Consider the first triple <b0, 000, True>, we have to prove the following 6 properties, in which $OT<<WOT$ means that the (strong) open transition $OT$ is covered, in the sense
-of definition \ref{def-Weak-bisim}, by the weak transition $WOT$ (it could be a set, but this will not be used here):
-
-\bigskip
-\begin{minipage}{0.2\linewidth} 	 
-$SS_1 << WI_1$
-
-$SS_2 << WI_2$
-
-$SS_3 << WI_3$
-\end{minipage}
-\hspace{1cm}
-\begin{minipage}{0.4\linewidth}
-$SI_1 << WS_1$
-
-$SI_2 << WS_2$
-
-$SI_3 << WS_3$
-\end{minipage}
-
-\bigskip
-
-         Note: if we were using the alternative Weak bisim from Appendix \ref{app-WFH-equiv}, Lemma \ref{lem-rel-OT-WOT}, that is checking strong bisimulation between the corresponding 
-weak automaton, we would have a more transitions coverage to examine, as we have 4 weak transitions for $b0$ in the specification weak automaton, and 7 WOTs (including 4 
-parameterized WOTs) from 000 in the implementation automaton.
-
-Preliminary remarks:
-  \begin{itemize}
-    \item Both pNets trivialy verify the ``non-observability''
-      condition: the only vectors having $\tau$ as an action of a
-      sub-net are of the form ``$< -, \tau, -> -> \tau$''.
-    \item We must take care of variable name conflicts: in our example, the variables of the 2 systems already have different names, but the action parameters occurring in the 
-transitions (m, msg, ec) are the same, that is not correct. In the tools, this is managed by the static semantic layer; in the following example, we have renamed all conflicting 
-variables using suffix 1 for the Specification, and 2 for the Implementation.
-    \end{itemize}
-
-  In our running example in page \pageref{subsubsection:runnig example}, we have shown the proof for one of the
-transitions of ($\text{b0},  202,  True$), namely that $SS_3$ is covered by $WI_3(0)$.
-We give here another example with $SS_1 << WI_1$, from the first triple ($\text{b0},  000,  True$). It includes less trivial predicates in the OTs:
-
-  $ SS_1 = \openrule
-  {\{\texttt{P}\mapsto \texttt{p-a1}\}, 
- [\forall \texttt{m1}. \texttt{p-a1} \neq \texttt{p-send(m1)} ], ()}
-  {\text{b0} \OTarrow {\nounderline{\texttt{p-a1}}} \text{b0}}
-  $
-
-$ WI_1 = \openrule
-  {\{\texttt{P}\mapsto \texttt{p-a2}\}, 
- [\forall \texttt{m2}. \texttt{p-a2} \neq \texttt{p-send(m2)} ], ()}
-{000 \OTWeakarrow {\texttt{p-a2}} 000}$
-
-  Let us check formally the conditions:
-
-\begin{itemize}
-  \item Their sets of active (non-silent) holes is the same: $J' = J_x = \{\texttt{P}\}$.
-  \item Triple ($\text{b0},  000,  True$) is in $\mathcal{R}$.
-  \item The verification condition \\
-    $\forall fv_{OT}. \{ \Pred \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
-   \left[\exists fv_{OT_x}.
-  \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
-     \!\land\! \alpha\!=\!\alpha_x\! \land\!  
-     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)\right]\}}$
-
-\medskip Gives us:
-
-$\forall \texttt{p-a1}. \{True \land \forall \texttt{m1}. \texttt{p-a1} \neq \texttt{p-send(m1)}\\
- \hspace{3mm} \implies \exists \texttt{p-a2}. 
-(\texttt{p-a1} = \texttt{p-a2}
-\land \forall \texttt{m2}. \texttt{p-a2} \neq \texttt{p-send(m2)}
-\land \nounderline{\texttt{p-a1}} = \nounderline{\texttt{p-a2}} 
-\land True\}$
-
-\medskip That is trivially true, choosing \texttt{p-a2=p-a1} for each given \texttt{p-a1}.
-
-\end{itemize}
-
-  \bigskip
-  All others pairs from this set are just as easily proven true.
-
-  \subsection{Test}
-
-  $<1,2,3>$
-
-  $\left< 1,2,3 \right>$
-
 \end{document}

### 2020-10-16 SujetStage/2020-pNetsubjectM2.tex
1st draft sujet de stage

\documentclass[11pt,fleqn]{article}
\usepackage{graphicx,url}
\usepackage{subfigure}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}

\oddsidemargin 0cm
\evensidemargin 0cm
\topmargin -0.5cm
%\textheight 23cm  %\advance\textheight by \topskip 
%\textwidth 18.5cm
% current ---
\textheight 21cm  %\advance\textheight by \topskip 
\textwidth 16cm
\raggedbottom

%\usepackage{scrpage2,lastpage,tikz,
\usepackage{url,amsmath}

%\graphicspath{{../../logos/}{./figs/}}
%
%\newcommand{\logos}{%
%  \begin{tikzpicture}[remember picture,overlay]
%    \node [yshift=-1cm] at (current page.north) [below] 
%      {\includegraphics[height=15mm]{logo_lip}%\hspace*{2cm}
%%        \includegraphics[height=15mm]{citi}
%
%};
% \end{tikzpicture}}
%\newcommand{\adresse}{%
%  \begin{tikzpicture}[remember picture,overlay]
%    \node [yshift=1cm] at (current page.south) [above] 
%       {\begin{tabular}{c}
%
%        \textsf{\textup{\color{blue}
%          LIP -- UMR CNRS / ENS Lyon / UCB Lyon 1 / INRIA -- 69007
%          Lyon  %et         CEA Tech - LIST
%        }}\\
%        \textsf{\textup{\color{blue}
%         %- +33 (0)3 59 57 78 24
%         % -- Fax. : +33 (0)3 28 77 85 37
%          Contact E-mail : amaury.maille@ens-lyon.fr -- matthieu.moy@univ-lyon1.fr -- ludovic.henrio@ens-lyon.fr}}
%      \end{tabular}};
% \end{tikzpicture}}

\thispagestyle{empty}

\begin{document}
\begin{center}
\resizebox{0.5\textwidth}{!}{\bf Internship subject (Master 2 or Master 1)}
\\\bigskip
\resizebox{\textwidth}{!}{\bf Refinement for open automata}
%  Systolisation d'un réseau de processus polyédrique}
\end{center}
\medskip

\begin{description}
\item[\bf Main advisor:] Rabéa Ameur Boulifa 
\item[\bf Co-advisors:] Ludovic Henrio and Eric MAdelaine
\item[\bf Place:] Eurecom  -- Sophia Antipolis
\\
OR\\
Laboratoire de l'Informatique du Parallélisme (LIP) --
  \'Ecole Normale Supérieure de Lyon
\end{description}

\subsection*{Context}

Establishing equivalences or refinement relations between programs or system is crucial both for verifying correctness of programs, by establishing that one implementation is the refinement of a specification.

In the previous years, we have studied theoretical foundations for open
systems and our formalism, called open automata, is able to represent operators of composition of processes, 
they are represented
as hierarchically composed automata with holes and parameters. 
Our long 
term goal is to 
develop a methodology combining symbolic operational semantic and bisimulation 
equivalences with deductive reasoning on the data part, 
and in practice combining bisimulation algorithms with SMT solvers to get automatic 
procedures proving equational properties
of these open systems. In the last years, we designed a weak bisimulation theory for  open automata and a translation from a specification language that we used, called pNets, to open automata~\cite{arxiv-weakbisim}.

Among the properties of our formalisms, we are interested in compositionality: If two systems are proven equivalent they will be undistinguishable by their context, and they will also be undistinguishable when their holes are filled with equivalent systems.
The article is illustrated with a transport protocol running example; it shows the characteristics of our formalism and our bisimulation relations.

\subsection*{Objectives}

The main objective of the internship is to study refinement theory for open automata. blablabla

The internship will start with a study of the semantics of a simple language called value passing CCS. The first objective of this internship is to design a semantics value passing CCS in terms of open automata. From this point we will be able to extend the semantics by taking into account the semantics of operators for composing CCS processes.

After this preliminary step, the next objective will be to design a refinement theory for open automata ........

The next steps in the internship will rely on these two initial works; they will consist in addressing some of the following (independent) objectives:
\begin{itemize}
\item express and prove compositionality properties for refinement relation over open automata.
\item Study formally the behaviour of CCS operators wrt refinement
\item  ...
\item ???
\end{itemize}

\begin{thebibliography}{9}
\bibitem{henrio:Forte2016}
Henrio, L., Madelaine, E., Zhang, M.:
\newblock {A Theory for the Composition of Concurrent Processes}.
\newblock In Albert, E., Lanese, I., eds.: {36th International Conference on
  Formal Techniques for Distributed Objects, Components, and Systems (FORTE)}.
  Volume LNCS-9688 of Formal Techniques for Distributed Objects, Components,
  and Systems., Heraklion, Greece (June 2016)  175--194

\bibitem{hou:hal-02406098}
Hou, Z., Madelaine, E.:
\newblock {Symbolic Bisimulation for Open and Parameterized Systems}.
\newblock In: {PEPM 2020 - ACM SIGPLAN Workshop on Partial Evaluation and
  Program Manipulation}, New-Orleans, United States (January 2020)

\bibitem{ameurboulifa2020compositional}
Rabéa Ameur-Boulifa and Ludovic Henrio and Eric Madelaine:
\newblock {Compositional equivalences based on Open pNets}.
\newblock arXiv {2007.10770} (2020)
\end{thebibliography}

\end{document}

### 2020-10-19 SujetStage/2020-pNetsubjectM2.tex
refs et...

@@
 \item[\bf Main advisor:] Rabéa Ameur Boulifa 
-\item[\bf Co-advisors:] Ludovic Henrio and Eric MAdelaine
+\item[\bf Co-advisors:] Ludovic Henrio and Eric Madelaine
 \item[\bf Place:] Eurecom  -- Sophia Antipolis
 \\
-OR\\
+or\\
 Laboratoire de l'Informatique du Parallélisme (LIP) --
@@
 
-The main objective of the internship is to study refinement theory for open automata. blablabla
-
+The main objective of the internship is to study refinement theory for open automata.  
+Our purpose is to define a refinement relation between the symbolic models allowing refinement verification for a class of parameterized systems.
 The internship will start with a study of the semantics of a simple language called value passing CCS.
@@
 
-After this preliminary step, the next objective will be to design a refinement theory for open automata ........
+After this preliminary step, the next objective will be to design a refinement theory for open automata.
+The purpose is to define the refinement semantics as a relation between open automata, that  can be classified in the van Glabbeek spectrum and can also be verified for finite state systems using an algorithmic method.
 
@@
 \begin{thebibliography}{9}
+
+\bibitem{Bellegarde:MEMOCODE2003}
+Fran{\c{c}}oise Bellegarde,Celina Charlet and Olga Kouchnarenko:
+\newblock {How to Compute the Refinement Relation for Parameterized Systems}.
+\newblock 1st {ACM} {\&} {IEEE} International Conference on Formal Methods and Models for Co-Design {(MEMOCODE} 2003), 24-26 June 2003, Mont Saint-Michel, France
+
 \bibitem{henrio:Forte2016}

### 2020-10-19 SujetStage/2020-pNetsubjectM2.tex
over skype

@@
 of these open systems.
-In the last years, we designed a weak bisimulation theory for  open automata and a translation from a specification language that we used, called pNets, to open automata~\cite{arxiv-weakbisim}.
+In the last years, we designed a weak bisimulation theory for  open automata and a translation from a specification language that we used, called pNets, to open automata~\cite{arxiv-weakbisim,henrio:Forte2016,hou:hal-02406098}.
 
@@
 Our purpose is to define a refinement relation between the symbolic models allowing refinement verification for a class of parameterized systems.
+
 The internship will start with a study of the semantics of a simple language called value passing CCS.
@@
 After this preliminary step, the next objective will be to design a refinement theory for open automata.
-The purpose is to define the refinement semantics as a relation between open automata, that  can be classified in the van Glabbeek spectrum and can also be verified for finite state systems using an algorithmic method.
+We will make sure that this relation is specified in a constructive manner, so that an algorithm could be derived from the specification in the future.
+The relationship between refinement and automata composition should also play a major role in this definition.
+
+%The purpose is to define the refinement semantics as a relation between open automata that can be classified in  and we will make sure that an algorithm could be designed to verify refinement can also be verified for finite state systems using an algorithmic method.
 
@@
 \begin{itemize}
-\item express and prove compositionality properties for refinement relation over open automata.
-\item Study formally the behaviour of CCS operators wrt refinement
-\item  ...
-\item ???
+\item Express and prove compositionality properties for refinement relation over open automata.
+\item Study formally the behaviour of CCS operators wrt refinement.
+\item Study the classification of the refinement semantics in the van Glabbeek spectrum could also be studied.
+\item Design the algorithm that checks refinement between wo open automata.
 \end{itemize}
@@
 
-\bibitem{ameurboulifa2020compositional}
+\bibitem{arxiv-weakbisim}
 Rabéa Ameur-Boulifa and Ludovic Henrio and Eric Madelaine:

### 2020-10-19 SujetStage/2020-pNetsubjectM2.tex
skype 2

@@
 After this preliminary step, the next objective will be to design a refinement theory for open automata.
-We will make sure that this relation is specified in a constructive manner, so that an algorithm could be derived from the specification in the future.
+We will make sure that this relation is specified in a constructive manner, so that an algorithm could be derived from the specification in the future~\cite{Bellegarde:MEMOCODE2003}.
 The relationship between refinement and automata composition should also play a major role in this definition.
@@
 \item Study formally the behaviour of CCS operators wrt refinement.
-\item Study the classification of the refinement semantics in the van Glabbeek spectrum could also be studied.
-\item Design the algorithm that checks refinement between wo open automata.
+\item Compare this theory with the state of the art and classify the refinement semantics in the van Glabbeek spectrum.
+\item Design the algorithm that checks refinement between two open automata.
 \end{itemize}

### 2020-10-20 SujetStage/2020-pNetsubjectM2.tex
corrections Eric

@@
 \begin{description}
-\item[\bf Main advisor:] Rabéa Ameur Boulifa 
+\item[\bf Main advisor:] Rabéa Ameur-Boulifa 
 \item[\bf Co-advisors:] Ludovic Henrio and Eric Madelaine
@@
 
-Establishing equivalences or refinement relations between programs or system is crucial both for verifying correctness of programs, by establishing that one implementation is the refinement of a specification.
+Establishing equivalences or refinement relations between programs or system is crucial  for verifying correctness of programs, by establishing that one implementation is the refinement of a specification.
 
 In the previous years, we have studied theoretical foundations for open
-systems and our formalism, called open automata, is able to represent operators of composition of processes, 
-they are represented
+systems and our formalism, called open automata, is able to represent operators of composition of processes,  represented
 as hierarchically composed automata with holes and parameters. 
@@
 Among the properties of our formalisms, we are interested in compositionality: If two systems are proven equivalent they will be undistinguishable by their context, and they will also be undistinguishable when their holes are filled with equivalent systems.
-The article is illustrated with a transport protocol running example; it shows the characteristics of our formalism and our bisimulation relations.
+The article \cite{arxiv-weakbisim} is illustrated with a transport protocol running example; it shows the characteristics of our formalism and our bisimulation relations.
 
@@
 The main objective of the internship is to study refinement theory for open automata.  
-Our purpose is to define a refinement relation between the symbolic models allowing refinement verification for a class of parameterized systems.
+Our purpose is to define a refinement relation between the symbolic models allowing refinement verification for a class of open systems.
 
@@
 The first objective of this internship is to design a semantics value passing CCS in terms of open automata.
-From this point we will be able to extend the semantics by taking into account the semantics of operators for composing CCS processes.
+Especially, we will be able to extend the semantics by taking into account the semantics of operators for composing CCS processes.
 
@@
 \begin{itemize}
-\item Express and prove compositionality properties for refinement relation over open automata.
+\item Express and prove compositionality properties for the refinement relation over open automata.
 \item Study formally the behaviour of CCS operators wrt refinement.
-\item Compare this theory with the state of the art and classify the refinement semantics in the van Glabbeek spectrum.
+\item Compare this theory with the state of the art of the refinement semantics.
 \item Design the algorithm that checks refinement between two open automata.
@@
 \bibitem{Bellegarde:MEMOCODE2003}
-Fran{\c{c}}oise Bellegarde,Celina Charlet and Olga Kouchnarenko:
+Fran{\c{c}}oise Bellegarde, Celina Charlet and Olga Kouchnarenko:
 \newblock {How to Compute the Refinement Relation for Parameterized Systems}.
-\newblock 1st {ACM} {\&} {IEEE} International Conference on Formal Methods and Models for Co-Design {(MEMOCODE} 2003), 24-26 June 2003, Mont Saint-Michel, France
+\newblock 1st {ACM} {\&} {IEEE} International Conference on Formal Methods and Models for Co-Design {(MEMOCODE} 2003), 24-26 June 2003, Mont Saint-Michel, France. 
+\newblock DOI: 10.1109/MEMCOD.2003.1210095
 
@@
   Volume LNCS-9688 of Formal Techniques for Distributed Objects, Components,
-  and Systems., Heraklion, Greece (June 2016)  175--194
+  and Systems., Heraklion, Greece (June 2016)  175--194. 
+\newblock  \url{https://hal.inria.fr/hal-01299562}
 
@@
 \newblock In: {PEPM 2020 - ACM SIGPLAN Workshop on Partial Evaluation and
-  Program Manipulation}, New-Orleans, United States (January 2020)
+  Program Manipulation}, New-Orleans, United States (January 2020). 
+ \newblock \url{https://hal.inria.fr/hal-02406098}
 
@@
 \newblock {Compositional equivalences based on Open pNets}.
-\newblock arXiv {2007.10770} (2020)
+\newblock arXiv {2007.10770} (2020).
+ \newblock \url{https://arxiv.org/abs/2007.10770}
 \end{thebibliography}

### 2021-03-18 2021-Refinement/rapport.tex
Refinement v0a

\documentclass{article}

\usepackage{xunicode}
\usepackage{fontspec}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{unicode-math}
\AtBeginDocument{\renewcommand\setminus{\smallsetminus}}
\usepackage{polyglossia}
\setmainlanguage{english}

\theoremstyle{plain}
\newtheorem{thm}{Theorem}
\newtheorem{cor}{Corollary}
\newtheorem{prop}{Proposition}

\theoremstyle{definition}
\newtheorem{defi}{Definition}
\newtheorem{exi}{Example}

\newcommand\nmm[1]{\(\displaystyle #1\)}
\newcommand\setR{\mathbb{R}}
\newcommand\setZ{\mathbb{Z}}
\newcommand\setN{\mathbb{N}}
\newcommand\mpar[1]{{\left(#1\right)}}
\newcommand\mbrk[1]{{\left[#1\right]}}
\newcommand\mbrc[1]{{\left\{#1\right\}}}
\newcommand\mdbrk[1]{\left⟦#1\right⟧}
\newcommand\card[1]{{\left|#1\right|}}
\newcommand\psubst[1]{\mbrc{\!\!\mbrc{#1}\!\!}}
\newcommand\subst[2]{\mbrk{#1\middle/#2}}
\newcommand\choice[1]{\left\{\everymath{\displaystyle}%
	\begin{array}{lr}#1\end{array}\right.}
\newcommand\midbar{\,\middle|\,}
\newcommand\mset[2]{\mbrc{#1\midbar #2}}
\newcommand\prel[4]{\mbrk{#2\mathrel{#1}#3\midbar #4}}
\newcommand\subbox[1]{{\makebox[.5\width]{\(\scriptstyle #1\)}}}
\newcommand\bigsymb[2][\Large]{\text{#1\nmm{#2}}}
\newcommand\defnotation{\DOTSB\;{\Colon=}\;}
\newcommand\defobject{\DOTSB\;{\coloneq}\;}
\newcommand\nwedge{\DOTSB\;{\wedge}\;}
\newcommand\qwedge{\DOTSB\quad{\wedge}\quad}
\newcommand\sat{{\vdash}}
\newcommand\fvars[1]{{\mathit{vars}\mpar{#1}}}
\newcommand\fterms[1]{{\mathcal{T}\mpar{#1}}}
\newcommand\fcterms[1]{{\mathcal{T}_{\makebox[1pt][r]{\(\scriptstyle 0\)}}\mpar{#1}}}
\newcommand\fformulas[1]{{\mathcal{F}\mpar{#1}}}
\newcommand\fcformulas[1]{{\mathcal{F}_{\makebox[1pt][r]{\(\scriptstyle 0\)}}\mpar{#1}}}
\newcommand\fvalues[1]{{\mathcal{P}\mpar{#1}}}
\newcommand\OA[7]{\left<#1,#2,#3,#4, #5,#6,#7\right>}
\newcommand\OT[6]{\text{\small\(%
	\setlength\arraycolsep{2pt}\everymath{\displaystyle}%
	\begin{array}{c}%
	#4,#5,#6 \\\hline
	#1\xrightarrow{\raisebox{-1.5pt}[.8\height][0pt]{\makebox[1.4\width]{\(\scriptstyle #3\)}}}#2
	\end{array}\)}}
\newcommand\OTx[4]{\OT{s_{#1}}{s'_{#1 #2}}{\alpha_{#1 #2}}{\beta_{#3 j}^{j \in J'_{#4}}}{g_{#1 #2}}{\psi_{#1 #2}}}
\newcommand\OTg{\OTx{}{}{}{}}

% possible examples for refinement: + <= |, ; <= |

\title{Refinement for open automata}
\author{Quentin \textsc{Corradi}}

\begin{document}
\maketitle

\section{Introduction}
Open automata are used to give an interpretation for open pNets.
% TODO: expand

\section{Notations}
Throughout this paper, tuples might be denoted differently depending on what they represent.
Quantification will be used loosely, any previously defined object in a quantification means that the object is constrained to have that previous value, and any undefined object is defined by the quantifier.
For instance \(\forall \mpar{x, y} \in \setZ^2, \exists \mpar{x', y} \in \setR^2, P\) means \(\forall \mpar{x, y}, \exists \mpar{x', y'}, y = y' \wedge P\).

Family of values, or equivalently maps will be noted \(\mset{i \mapsto x_i}{i \in I}\), \(\mset{i \gets x_i}{i \in I}\) or \(x_i^{i \in I}\).
The latter will only be used when unambiguous; for instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\), but \(\mbrc{\alpha \mapsto 1, \beta \mapsto 2, \gamma \mapsto 3}\) must be represented with one of the two first notation.
The disjoint union of two maps \(\varphi \in X^I\) and \(\psi \in Y^J\) with \(I \cap J = \emptyset\) is \(\varphi \uplus \psi \in \mpar{X \cup Y}^{I \uplus J}\).

A function with two parameters \(R \in X \times Y \to Z\) might be noted using the relational notation \(\prel{R}{x}{y}{z}\) when it is relevant for noting \(R\mpar{x, y} = z\) or equivalently \(\mpar{x, y, z} \in R\).

\section{Open Automaton}
To define an open automaton we need some preliminary definitions.
\begin{defi}[Expression algebra]
An expression algebra \(E\) is a disjoint union \(E \defobject \mathcal{T} \uplus \mathcal{F}\) where \(\mathcal{T}\) is a term algebra and \(\mathcal{F}\) the formulas over \(\mathcal{T}\).

%TODO: there might be binders in expressions, vars = free veriables, quantifiers are also allowed
We also define convenience notations \(\fterms{E} \defnotation \mathcal{T}\) and \(\fformulas{E} \defnotation \mathcal{F}\).
\end{defi}
The terms algebra is arbitrary.
The formulas form a propositional logic over terms in \(\mathcal{T}\) and some relations, or equivalently they are first order logic formulas without quantifiers but free variables are allowed.
An example of term algebra can be Peano integers (zero, variable and successor function), the formulas associated can use the relations equality, \(\mathit{sum}\mpar{a, b, c} \defobject a = b + c\) and \(\mathit{prod}\mpar{a, b, c} \defobject a = b \times c\).
\begin{defi}[Variables, Closed terms/formulas]
\(\fvars{e}\) is the set of variables in \(e \in E\).
The closed terms are \(\fcterms{E} \defnotation \mset{t \in \fterms{E}}{\fvars{t} = \emptyset}\); \(\fcterms{E} \subset \fterms{E}\).
The closed formulas are \(\fcformulas{E} \defnotation \mset{f \in \fformulas{E}}{\fvars{f} = \emptyset}\); \(\fcformulas{E} \subset \fformulas{E}\).
\end{defi}
More generally a closed expression is an expression without variable.
In a standard context it would be without free variables but here the ``no quantifier" constraint means that there is no such thing as ``bound variables".
\begin{defi}[Interpretation, Values, Satisfaction, (Parallel) substitution]
We assume that the following functions are given:
\begin{itemize}
\item The interpretations of closed terms, \(\mdbrk{\_} \in \fcterms{E} \to \fvalues{E}\), with \(\fvalues{E}\) a set of interpreted value of terms;
\item The satisfaction of closed formulas, \(\sat \in \fcformulas{E} \to \mbrc{0, 1}\);
\item The substitution in \(e \in E\) of \(x \in \fvars{e}\) by \(t \in \fterms{E}\), \(e\subst{t}{x}\);
\item The parallel substitution in \(e \in E\) of variables in \(V\) by \(\psi \in \fterms{E}^V\), \(e\psubst{\psi}\).
% \item The formula interpretation of any variable assignement \(\psi \in \fterms{E}^V\), \nmm{\mdbrk{\psi} \defnotation \bigwedge_{v \in V} v = \psi\mpar{v}}; \(\mdbrk{\psi} \in \fformulas{E}\).
\end{itemize}
\end{defi}
The set \(V\) is not required to be a subset of \(\fvars{e}\).
In the case \(U \defobject V \setminus \fvars{e}, U \neq \emptyset\), the variables in \(U\) are not substituted.
The substitutions might give a nonsensical expression; for instance terms can be integers and pairs with addition, \(\mpar{a + b}\psubst{a \mapsto 7, b \mapsto \mpar{4, 5}}\) is not a valid term.
This can be guarded with \(e\subst{t}{x} \in E\) and \(e\psubst{\psi} \in E\) when there is quantification on \(t\) and \(\psi\); in the other cases it is supposed to give a valid expression.
The interpretation of values and satisfaction are supposed to be decidable.
We are not interested in how \(\fvalues{E}\) is defined.
Whether it is predefined or caracterised by \(\fvalues{E} \defnotation \mdbrk{\fcterms{E}}\) is not the point of this definition.
A value \(v\) may be used for keeping a variable state, and then injected in terms for substitution.
While this is correct when \(\fvalues{E} \subseteq \fcterms{E}\), in the other cases this will be used as a shorthand for substitution with any \(t \in \mdbrk{v}^{-1}\).
\begin{defi}
The following notations will be used for convenience:
\begin{itemize}
\item Let \nmm{f \in \fcformulas{E}}, \nmm{\vdash f_0 \defnotation \sat\mpar{f_0} = 1} and \nmm{\nvdash f_0 \defnotation \sat\mpar{f_0} = 0};
\item Let \nmm{f \in \fformulas{E}, \sigma \in \fvalues{E}^V}, \\
	\nmm{\sigma \vdash f \defnotation \exists \varphi \in \fvalues{E}^{\fvars{f} \setminus V}, f\psubst{\sigma \uplus \varphi} \in \fcformulas{E} \nwedge \vdash f\psubst{\sigma \uplus \varphi}}.
\end{itemize}
\end{defi}
% TODO: redo that explaination
The first notation is quite classical when satisfaction is defined as a relation rather than a function.
The second notation means that the disjunction of the right formulas is satisfiable, not necessarily with the same value for a variable name between formulas, for all valid valuation of the left formula.
\begin{defi}[Formulas combination, Expression algebra combination]
The propositional logic built without existential quantifiers on top of two propositional logics \(\fformulas{E_1}\) and \(\fformulas{E_2}\) is \(\fformulas{E_1} + \fformulas{E_2}\).
By extension \(E_1 + E_2 \defnotation \mpar{\fformulas{E_1} + \fformulas{E_2}} \uplus \mpar{\fterms{E_1} \cup \fterms{E_2}}\).
\end{defi}

With these common definitions and notations settled, the objects of interest can now be defined.
\begin{defi}[Open automaton]
An open automaton is a tuple \(\OA{S}{i}{E}{V}{\varphi}{J}{T}\) with \(S\) the set of states, \(i \in S\) the initial state, \(E\) an expression algebra, \(V\) the set of variable names unique to this automaton, \(\varphi \in \fvalues{E}^V\) the initial valuation of variables, \(J\) the set of hole names and \(T\) a set of open-transitions.

\(S, V, J\) are arbitrary sets, only \(J\) is required to be finite.
\end{defi}
The variable names may clash when considering two automaton, in that case we suppose that we can still distinguish the variables.
All the possible open transitions, from which transitions in \(T\) are selected, are defined below.
\begin{defi}[Open transition]
An open transition is a tuple \nmm{\OT{s}{s'}{\alpha\mpar{v_\alpha}}{\mpar{\beta_j\mpar{v_{\beta j}}}^{j \in J'}}{g}{\psi}} with \(s, s' \in S\) the source and target states, \(\alpha \in A\) an action label, \(J' \subseteq J\) the holes involved, \(\beta_j \in A\) the action labels of the holes, \(v_\alpha, v_{\beta j}^{j \in J'}\) fresh distinct variables, \(g \in \fformulas{E}\) the guard and \(\psi \in \fterms{E}^V\) the new value of the variables.

The set of action labels \(A\) is arbitrary and implicit.
To simplify formulas, the notations \(\alpha \defnotation \alpha\mpar{v_\alpha}\) and \(\alpha = \beta \defnotation \alpha = \beta \wedge v_\alpha = v_\beta\) will be used.
The guard and new values of the variables can use any defined variable: \nmm{\bigcup_{v \in V} \fvars{\psi\mpar{v}} \cup \fvars{g} \subseteq V \cup \mbrc{v_\alpha} \cup \mset{v_{\beta j}}{j \in J'}}.
\end{defi}
Now we can define some utilitary functions:
\begin{defi}[Guard, Variables, Out-transition, In-transition]
\(\mathrm{OT}\mpar{s}\) are called the out-transitions of \(s\) and \(\mathrm{IT}\mpar{s}\) and its in-transitions.
\begin{align*}
	\mathit{guard}\mpar{\OTg} & \defnotation g & \mathit{}
	\fvars{\OT{s}{s'}{\alpha\mpar{v_\alpha}}{\mpar{\beta_j\mpar{v_{\beta j}}}^{j \in J'}}{g}{\psi}} & \defnotation \mbrc{v_\alpha} \cup \mset{v_{\beta j}}{j \in J'} \\
	\mathrm{OT}\mpar{s} & \defnotation \mbrc{\OTg \in T} &
	\mathrm{IT}\mpar{s'} & \defnotation \mbrc{\OTg \in T}
\end{align*}
\end{defi}
The intuition of an open automaton is a partially defined LTS with variables, guards on transitions and parametrised actions.

\section{Semantic and composition of Open Automata} % This is taken from 2007.10770.pdf
% Intro section
% \begin{defi}[Run of an open autmaton]
% A run of an open automaton \(\mathrm{OA}_c \defobject \OA{S}{i}{E}{V}{\varphi}{J}{T}\) is a list \(\rho\) of pairs \(\forall k, \rho\mbrk{k} \defobject \mpar{t_k, \nu_k}\) with \(t_k \in T, \nu_k \in \fcterms{E}^\fvars{t_k}\) such that:

% Let \nmm{t_k \defnotation \OTx{k}{}{k}{k}},
% \begin{itemize}
% \item \(\forall k, s_k = \choice{i & k = 0 \\ s'_{k-1} & k > 0}\);
% \item \(\forall k, \sigma\mpar{\rho}\mbrk{k} \defnotation \choice{\varphi & k = 0 \\ \sigma\mpar{\rho}\mbrk{k-1}\psubst{\psi_{k-1}}\psubst{\nu_{k-1}} & k > 0}\), \(\sigma\mpar{\rho}\mbrk{k} \in \fvalues{E}^V\);
% \item \(\vdash g_k\psubst{\sigma\mpar{\rho}\mbrk{k} \uplus \nu_k}\).
% \end{itemize}
% \end{defi}
% Explain what a run is and what purpose each element serves.
When the auomaton is in a state \(s \in S\) with a valuation of its variables \(\sigma \in \fvalues{E}^V\), it cannot perform transitions \nmm{t \defobject \OTg \in T} such that \(\nvdash g\psubst{\sigma}\).
After performing the transition and emitting action \(\alpha\), the automaton is in the state \(s'\) with valuation \(\psi\psubst{\sigma \uplus \varphi}\) for some \(\varphi \in \fvalues{E}^\fvars{t}\).
The holes are synchronised using a handshake like mecanism when the transition happens.
\begin{exi} % Examples
\end{exi}

An open automaton can be partially specified, the partial specification comes from the holes.
A hole can be filled with an open automaton, this operation is called composition.
\begin{defi}[Composition of open automata]
The composition of \(\mathrm{OA}_c \defobject \OA{S_c}{i_c}{E_c}{V_c}{\varphi_c}{J_c}{T_c}\) in the hole \(k \in J_p\) of \(\mathrm{OA}_p \defobject \OA{S_p}{i_p}{E_p}{V_p}{\varphi_p}{J_p}{T_p}\) is:
\begin{align*}
	\mathrm{OA}_p\subst{\mathrm{OA}_c}{k} \defnotation & \OA{S_p \times S_c}{\mpar{i_p, i_c}}{E_p + E_c}{V_p \uplus V_c}{\varphi_p \uplus \varphi_c}{J_c \uplus J_p \setminus \mbrc{k}}{T} \\
	\text{With } T \defobject & \mset{\OT{\mpar{s_p, s_c}}{\mpar{s'_p, s'_c}}{\alpha_p}{\beta_j^{j \in J'_c \uplus J'_p \setminus \mbrc{k}}}{g_p \wedge g_c \wedge \alpha_c = \beta_k}{\psi_p \uplus \psi_c}}{\OTx{p}{}{}{p} \in T_p, \OTx{c}{}{}{c} \in T_c} \\
	& \cup \mset{\OT{\mpar{s_p, s_c}}{\mpar{s'_p, s_c}}{\alpha_p}{\beta_j^{j \in J'_p}}{g_p}{\psi_p}}{\OTx{p}{}{}{p}, k \notin J', s_c \in S_c}
\end{align*}
Similarly to expression substitution, the parallel composition is noted \(\mathrm{OA}\psubst{\mathrm{OA}_j^{j \in J}}\).
\end{defi}
The actions emitted when \(\mathrm{OA}_c\) makes a transition is sychronised with the action of the hole \(k\) in transitions of \(\mathrm{OA}_p\) which have it as a hole actions (first transition set, \(\alpha_c = \beta_k\)).
No transition of \(\mathrm{OA}_c\) is performed when a transition that do not refer to the hole \(k\) is performed in \(\mathrm{OA}_p\) (second transition set, \(k \notin J'\)).
The composition may look like a handshake, with both automata running in parallel (product of states and joint variables) but it is actually not symmetric.
\begin{exi} % TODO: Examples
\end{exi}

\section{What is a refinement for Open Automata} % TODO
% Re-read what refinement are used for
There are several properties that we may want from a refinement relation.
Depending on these properties, several kind of refinement may be used.
For example if we are interested in being able to produce the same sequence of action we may want to use trace set inclusion as a refinement.
% simulation refinement, hole type refinement, control refinement, (meet semi)lattice refinement (meet=handshake a <= b <=> a = a || b, join=non-det choice), action refinement

The important properties we will consider here are:
\begin{description}
\item[Reflexivity:] \(\forall a, a \leq a\);
\item[Transitivity:] \(\forall a\, b\, c, a \leq b \wedge b \leq c \implies a \leq c\);
\item[Preorder:] Reflexivity and transitivity;
\item[Composition is a refinement:] \(\forall a\, b, a\mbrk{b} \leq a\);
\item[Composition context equivalence:] \(\forall a\, b\, c, a \leq b \wedge a\mbrk{c} \leq a \implies a\mbrk{c} \leq b\mbrk{c}\);
\item[Composition congruence:] \(\forall a\, b\, c, a \leq b \wedge c\mbrk{a} \leq c \implies c\mbrk{a} \leq c\mbrk{b}\);
\item[Composition compatibility:] \(\forall a\, b\, c\, d, a \leq b \wedge c \leq d \wedge c\mbrk{a} \leq c \implies c\mbrk{a} \leq d\mbrk{b}\);
\item[FH-bisimulation compatibility:] \(\forall a\, b\, c, d, a = b \wedge c = d \wedge a \leq c \implies b \leq d\).
\end{description}
The interesting but not necessary properties are:
\begin{description}
\item[Deadlock preservation:] If \(a \leq b\) then \(a\) does not introduces new deadlocks.
\end{description}
Deadlock preservation conflicts with ``composition is a refinement" by disallowing some unwanted cases where an automaton in a hole cannot produce any action that out-transitions expect.
In particular filling a hole with the deadlock automaton (one state without out-transitions) is not considered a refinement for a deadlock preserving refinement.
This property has another impact which lead to write prerequisites like \(a \leq b \wedge a\mbrk{c} \leq a \implies a\mbrk{c} \leq b\mbrk{c}\) for context equivalence because \(a\mbrk{c} \leq a\) might not be true.

On the other hand the interesting but actually unwanted properties are:
\begin{description}
\item[Daisy equivalence:] Filling a hole of \(a\) with a daisy gives \(b\) such that \(a \leq b \wedge b \leq a\), i.e. it is not a strict refinement.
\end{description}
While daisy equivalence might seem to be a natural property because the daisy being the meaning of a hole, there is actually a difference between the two.
Daisy equivalence allows to refine by filling a daisy but also by going the other way, that is putting new action restrictions to any transition (and duplicating transitions).
The issue especially arise when two independant holes are filled with a daisy, then the other way is simulated by putting back the actions but as a unique hole, effectively merging independant holes.
% TODO: Expand on why not to do that

% refinement on Open Automata
% Caveat (is blablabla a strict refinement) and what we may want (trace/run safety)
% Working definition next section

\section{Refinement relation}
The main objective of the refinement relation in this section is to be able to say that a composition is a refinement of the base automaton (\(a\mbrk{b} \leq a\)).
However composing an open automaton can give an automaton where not much can be said in terms of hole indicies.
So looking at restricted cases where holes are related in a specific manner can help understanding the general case.
For two open automata \(\mathrm{OA}_1 \defobject \OA{S_1}{i_1}{E_1}{J_1}{V_1}{\varphi_1}{T_1}\) and \(\mathrm{OA}_2 \defobject \OA{S_2}{i_2}{E_2}{J_2}{V_2}{\varphi_2}{T_2}\), the following refinement relations are defined.

This relation is the basis for all the following ones.
It applies on automaton with same holes.
The goal is to caracterise automata that have a more determined behaviour (more deterministic) without adding deadlocks.
\begin{defi}[Hole-identical refinement]
If \(J_1 = J_2\) then ``\(\mathrm{OA}_1\) is a hole-identical refinement of \(\mathrm{OA}_2\)" is defined, and its definition is as follows:
\begin{multline*}
	\mathrm{OA}_1 \leq_\equiv \mathrm{OA}_2 \defnotation \exists R \in \mpar{S_1 \times S_2} \to \fformulas{E}_1 + \fformulas{E}_2, \\
	\mpar{\exists p \in \fformulas{E}_1 + \fformulas{E}_2, \quad \prel{R}{i_1}{i_2}{p} \qwedge \vdash p\psubst{\varphi_1 \uplus \varphi_2}} \\
	\wedge R \text{ hole-identical simulation of } \mathrm{OA}_1 \text{ in } \mathrm{OA}_2
\end{multline*}
\end{defi}
As in other simulation-like relations, \(R\) can be seen as a witness of \(\mathrm{OA}_1 \leq_\equiv \mathrm{OA}_2\).
Hence when two open automata are in relation, such a simulation will be called a witness.
To be a witness the standard requirement is that \(R\) relates initial states, \(R\) is closed under progress and related states are simultaneously final.

In this model there is no final states so there is no need for that last part.
The progress closure is stated after as \(R\) being a hole-identical refinement relation.
The specificities of open automata comes in when relating the (initial) states.
The relation \(\prel{R}{i_1}{i_2}{p}\) means that \(i_1\) is related to \(i_2\) under the condition that the curent value of variables satisfies \(p\).
The predicate \(p\) is used to take into account the fact that a state is also constituted of the value of the variables.
This is already used in FH-bisimulation introduced in previous articles about open automata.
So it is normal to find right after \(\vdash p\psubst{\varphi_1 \uplus \varphi_2}\) which means that the initial valuation satisfies \(p\).
\begin{defi}[Hole-identical simulation]
``\(R\) is a hole-identical simulation of \(\mathrm{OA}_1\) in \(\mathrm{OA}_2\)" is defined as:
\begin{multline*}
	\forall \prel{R}{s_1}{s_2}{p}, \\
	\mpar{\everymath{\displaystyle}\begin{array}{l}
		\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{} \in T_2, p'_x \in \fformulas{E}_1 + \fformulas{E}_2}^{x \in X}, \\[12pt]
		\mpar{\forall x \in X, \prel{R}{s'_1}{s'_{2x}}{p'_x}} \wedge \forall \sigma \in \fvalues{E_1}^{V_1 \uplus \fvars{t_1}} \times \fvalues{E_2}^{V_2}, \\[6pt]
		\quad \sigma \vdash \mpar{p \wedge g_1 \implies \bigvee_{x \in X} \mpar{\alpha_1 = \alpha_{2x} \wedge \bigwedge_{j \in J'} \beta_{1j} = \beta_{2xj} \wedge g_{2x} \wedge p'_x\psubst{\psi_1 \uplus \psi_{2x}}}} \\[12pt]
	\end{array}} \\
	\wedge \sat\mpar{p \wedge \bigvee_\subbox{t_2 \in \mathrm{OT}\mpar{s_2}} \mathit{guard}\mpar{t_2} \implies \bigvee_\subbox{t_1 \in \mathrm{OT}\mpar{s_1}} \mathit{guard}\mpar{t_1}}
\end{multline*}
\end{defi}
Being stable wrt.\ progress is the same as stating that for all related states, transitions can be matched and target states are also related (two first lines).
For a bisimulation transitions are matched one-to-many from each automaton to the other, but for a simulation only one way is used.
There are some conditions to ensure that transitions are not matched to incompatible ones (3\textsuperscript{rd} line):
For all variable assignement of the two automata and all hole actions (\(\forall \sigma\) part), assuming that the states were related and the transition in \(\mathrm{OA}_1\) is possible (\(p \wedge g_1\) part) then there is always a transition, not necessarily only one, which can be performed (\(g_{2x}\)), produce the same action (\(\alpha_1 = \alpha_{2x}\)), accept the same action from the holes and satisfy the predicate for relating the target states after variable update (\(p'_x\psubst{\psi_1 \uplus \psi_{2x}}\)).

The notion of refinement here is stating that \(\mathrm{OA}_1\) is a refinement of \(\mathrm{OA}_2\) if \(\mathrm{OA}_1\) can be simulated in \(\mathrm{OA}_2\).
The hole-identical part is referring to the fact that holes indicies are the same and identical holes indicies have to perform the same actions.
On top of that the last line ensures deadlock preservation.
It can be interpreted ``assuming the predicate holds and there is any possible transition in \(\mathrm{OA}_2\) (= no deadlock), then there must be a possible transition in \(\mathrm{OA}_1\) (= no deadlock)".
It does not have to ensure that this transition isn't garbage because the first part of the simulation already does it.
Also if there was a deadlock then there is no transition because no trasition can be simulated in a deadlock, hence deadlock ``preservation" and not ``reduction".

\begin{exi} % TODO
\end{exi}

% TODO Properties: do not forget to add deadlock equivalence in the 3 theorems
\begin{thm}[Hole-identical refinement correction] % TODO
% Let \(\mathrm{OA}_1 \defobject \OA{S_1}{i_1}{E_1}{V_1}{\varphi_1}{J}{T_1}, \mathrm{OA}_2 \defobject \OA{S_2}{i_2}{E_2}{V_2}{\varphi_2}{J}{T_2}\) such that \(\mathrm{OA}_1 \leq_\equiv \mathrm{OA}_2\), for every run \(\) there is a run \(\) such that .
\end{thm}
\begin{proof}
\end{proof}
% For the completeness there are two case, either the states and value domains of the automata variables are finite or at least one is not.
% In the first case there is a constructive proof and in the other case a slight modification is required to get the completeness.
% \begin{thm}[Hole-identical refinement completeness, finite case] % TODO
% Let \(\mathrm{OA}_1 \defobject \OA{S_1}{i_1}{E_1}{V_1}{\varphi_1}{J}{T_1}, \mathrm{OA}_2 \defobject \OA{S_2}{i_2}{E_2}{V_2}{\varphi_2}{J}{T_2}\) such that \(S_1, S_2, \mdbrk{\fterms{E}_{01}}, \mdbrk{\fterms{E}_{02}}\) are finite and for every run \(\) there is a run \(\) such that , then \(\mathrm{OA}_1 \leq_\equiv \mathrm{OA}_2\).
% \end{thm}
% \begin{proof}
% \end{proof}
% The non-finite case requires more expressive formulas for the refinement simulation.
% The way I used to do that is to allow second order formulas with fixed sets and a relation \(y \in Y\).
\begin{defi}[Second order formulas]
Let \(E\) be an expression algebra, \(\mathit{SO}\mpar{\fformulas{E}}\) is an extension with pairs of terms, fixed sets and the set membership relation.
By extension \(\mathit{SO}\mpar{E} \defnotation \fterms{E} \uplus \mathit{SO}\mpar{\fformulas{E}}\).
\end{defi}
% \begin{thm}[Hole-identical refinement completeness, general case] % TODO
% Let \(\mathrm{OA}_1 \defobject \OA{S_1}{i_1}{E_1}{V_1}{\varphi_1}{J}{T_1}, \mathrm{OA}_2 \defobject \OA{S_2}{i_2}{E_2}{V_2}{\varphi_2}{J}{T_2}\) such that \(S_1, S_2, \mdbrk{\fterms{E}_{01}}, \mdbrk{\fterms{E}_{02}}\) are finite and for every run \(\) there is a run \(\) such that , then \(\mathrm{OA}_1 \leq'_\equiv \mathrm{OA}_2\).
% With \(R \in S_1 \times S_2 \to \mathit{SO}\mpar{E_1 + E_2}\) for the refinement simulation of \(\leq'_\equiv\).
% \end{thm}
% \begin{proof}
% \end{proof}
\begin{thm} The hole-identical refinement relation is a preorder. \end{thm}
\begin{proof}
\begin{description}
\item[Reflexivity:] Let \(\mathrm{OA}\) be an open automaton with variables in \(V\).
	The automaton variables on the right hand side of the relation will be noted \(v'\) for the equivalent variable \(v \in V\) in the automaton on the left hand side.
	The simulation \nmm{R = \mset{\mpar{s, s} \mapsto \bigwedge_{v \in V} v = v'}{s \in S_1}} is a witness of \(\mathrm{OA} \leq \mathrm{OA}\).
	Checking it is a simple exercise left to the reader in order to understand how the definition works.
\item[Transitivity:] Let \(\mathrm{OA}_1, \mathrm{OA}_2, \mathrm{OA}_3\) be open automata with respectively variables in \(V_1, V_2, V_3\).
	And let \(R_{12}\) be a witness of \(\mathrm{OA}_1 \leq_\equiv \mathrm{OA}_2\) and \(R_{23}\) be a witness of \(\mathrm{OA}_2 \leq_\equiv \mathrm{OA}_3\).
	\begin{align*}
		R_{13} \defobject & \mset{\mpar{s_1, s_3, \mathit{merge}_{V_1,V_3}\mpar{p_{12}, p_{23}}}}{\prel{R_{12}}{s_1}{s_2}{p_{12}} \wedge \prel{R_{23}}{s_2}{s_3}{p_{23}}} \\
		\mathit{merge}_{V_1,V_3}\mpar{p_{12}, p_{23}} \defobject & p_{12} \wedge p_{23} % TODO
	\end{align*}
\end{description}
\end{proof}

The goal of the following relation is to capture the case where holes are filled with automata that do not have any hole.
It is supposed to be a relation for which filling holes with fully specified automata is a considered refinement.
\begin{defi}[Hole-subset refinement]
If \(J_1 \subseteq J_2\) then ``\(\mathrm{OA}_1\) is a hole-subset refinement of \(\mathrm{OA}_2\)" is defined, and its definition is as follows:
\begin{multline*}
	\mathrm{OA}_1 \leq_\subseteq \mathrm{OA}_2 \defnotation \exists R \in \mpar{S_1 \times S_2} \to \fformulas{E}_1 + \fformulas{E}_2, \\
	\mpar{\exists p \in \fformulas{E}_1 + \fformulas{E}_2, \prel{R}{i_1}{i_2}{p} \wedge \vdash p\psubst{\varphi_1 \uplus \varphi_2}} \\
	\wedge R \text{ hole-subset simulation of } \mathrm{OA}_1 \text{ in } \mathrm{OA}_2
\end{multline*}
\end{defi}
This definitions is essentially the same as the hole-identical one excepted the constraint on holes which has been softened.

\begin{defi}[Hole-subset simulation]
\(R\) is a hole-subset simulation of \(\mathrm{OA}_1\) in \(\mathrm{OA}_2\) is defined as:
\begin{multline*}
	\forall \prel{R}{s_1}{s_2}{p}, \\
	\mpar{\everymath{\displaystyle}\begin{array}{l}
		\bigsymb{\forall} \OTx{1}{}{1}{1} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in T_2, p'_x \in \fformulas{E}_1 + \fformulas{E}_2}^{x \in X}, \\[12pt]
		\mpar{\forall x \in X, \prel{R}{s'_1}{s'_{2x}}{p'_x} \qwedge J'_1 = J'_{2x} \cap J_1} \\
		\quad \nwedge \mpar{p \wedge g_1} \vdash \mpar{\alpha_1 = \alpha_{2x} \wedge \bigwedge_{j \in J'_1} \beta_{1j} = \beta_{2xj} \wedge g_{2x} \wedge p'_x\psubst{\psi_1 \uplus \psi_{2x}}}^{x \in X} \\[12pt]
	\end{array}} \\
	\wedge \sat\mpar{p \wedge \bigvee_\subbox{t_2 \in \mathrm{OT}\mpar{s_2}} \mathit{guard}\mpar{t_2} \implies \bigvee_\subbox{t_1 \in \mathrm{OT}\mpar{s_1}} \mathit{guard}\mpar{t_2}}
\end{multline*}
\end{defi}
% TODO: Give an example of what you want to capture BEFORE and after the relation
% TODO: swap 1 <-> 2
The difference with the hole-identical simulation is that the holes involved in the matched transitions don't have to be exactly the same anymore.
The new constraint is that the holes in common (that is \(J'_1\)) should be involved at the same time and their action have to match.
What happens on the other holes is unspecified except for the fact that, by being free variables they still need to be valued such that the transition is possible.

An alternative version of this definition could enforce \(\exists J'_2 \subseteq J_2, \forall x \in X, J'_{2x} = J'_2\).
Let's call it the alternative hole-subset simulation.
This version would mean that the holes involved in every matched transitions must be the same.
While this may seem more natural this leads to the unwanted behaviour that an automaton FH-bisimilar to a refinement of some specification might not be a refinement of that specification:
\begin{prop}[Alternative hole-subset simulation is not compatible with FH-bisimulation]
TODO: collapse a transition that was differenciated by having one filled hole involved and it should be simple
\end{prop}
This is a sufficient reason to discard this version although it seems more natural.
\begin{prop}[Hole-subset refinement is compatible with FH-bisimulation]
% TODO
\end{prop}

% Hole-subset refinement can be used to specify behaviour/constraints on holes (like an API: first do anything not involving the api, then initialise the api, then do whatever you want that do not unload the api, then unload the api by returning to the first state), then have a relation for every hole with a different automata and this means well behaving with respect to the environement (holes)
\begin{exi} % TODO
\end{exi}

\begin{prop}[Hole-subset refinement is an extension of hole-identical refinement]
Hole-subset refinement and hole-identical match when holes are identical.
\end{prop}
\begin{proof}
% TODO: Proof that it behaves the same as the previous one when holes are identical
\end{proof}
\begin{prop}[Hole-subset refinement is a pre-order]
\end{prop}
\begin{proof}
\end{proof}
\begin{thm}[Composition is a refinement]
% TODO: Proof that filling holes with a fully specified automaton is a refinement
\end{thm}
\begin{proof}
\end{proof}
\begin{thm}[Context refinement]
% a <= b & a[c] <= a -> a[c] <= b[c]
\end{thm}
\begin{proof}
\end{proof}
\begin{thm}[Congruence with composition]
% a <= b & c[a] <= c -> c[a] <= c[b]
\end{thm}
\begin{proof}
\end{proof}

A relation for which filling holes with one hole open automata is a refinement.
\begin{defi}[Hole-matching refinement]
If \(\card{J_2} = \card{J_1}\) then ``\(\mathrm{OA}_2\) is a hole-matching refinement of \(\mathrm{OA}_1\)" is defined, and its definition is as follows:
\begin{multline*}
	\mathrm{OA}_2 \leq_\# \mathrm{OA}_1 \defnotation \exists R \in \mpar{S_1 \times S_2} \to \fformulas{E}_1 + \fformulas{E}_2, \quad f \in J_2 \setminus J_1 \to J_1 \setminus J_2, \\
	\mpar{\exists p \in \fformulas{E}_1 + \fformulas{E}_2, \prel{R}{i_1}{i_2}{p} \wedge \sat\mpar{\mdbrk{\varphi_1} \wedge \mdbrk{\varphi_2} \implies p}} \qwedge f\mpar{J_2 \setminus J_1} = J_1 \setminus J_2 \\
	\wedge R \text{ hole-f-matching simulation between } \mathrm{OA}_1 \text{ and } \mathrm{OA}_2
\end{multline*}
\end{defi}
This definitions is essentially the same as the hole-identical except that the constraint on holes has been softened and it is compensated with a invertible map between non-shared holes.

\begin{defi}[Hole-f-matching simulation]
\(R\) is a hole-f-matching simulation between \(\mathrm{OA}_1\) and \(\mathrm{OA}_2\) is defined as:
\begin{multline*}
	\forall \prel{R}{s_1}{s_2}{p}, \\
	\mpar{\everymath{\displaystyle}\begin{array}{l}
		\bigsymb{\forall} \OTx{2}{}{2}{2} \in T_2, \bigsymb{\exists} \mpar{\OTx{1}{x}{1x}{1x} \in T_1, p'_x \in \fformulas{E}_1 + \fformulas{E}_2}^{x \in X}, \\[12pt]
		\mpar{\forall x \in X, \prel{R}{s'_{1x}}{s'_2}{p'_x} \qwedge J'_2 \cap J_1 = J'_{1x} \cap J_2 \qwedge f\mpar{J'_2 \setminus J_1} \subseteq J'_{1x}} \\[4pt]
		\qquad \nwedge \mpar{p \wedge g_2} \vdash \mpar{\alpha_2 = \alpha_{1x} \wedge \bigwedge_\subbox{j \in J'_2 \cap J_1} \beta_{2j} = \beta_{1xj} \wedge g_{1x} \wedge p'_x\psubst{\psi_2 \uplus \psi_{1x}}}^{x \in X} \\[12pt]
	\end{array}} \\
	\wedge \sat\mpar{p \wedge \bigvee_\subbox{t_1 \in \mathrm{OT}\mpar{s_1}} \mathit{guard}\mpar{t_1} \implies \bigvee_\subbox{t_2 \in \mathrm{OT}\mpar{s_2}} \mathit{guard}\mpar{t_2}}
\end{multline*}
\end{defi}
% TODO: Matching a hole data with another hole is done with a_2=a_1x and constraint on respective variables, thus hole data is not uncontrained, same for action label because each transition has only 1 action label
% TODO: Explain what happens on holes constraints and action constraints
% J'_1x still necessary for the same reason essentially
% f() subset J'1 \ J2 : equality is possible and give a valid alternative that must match each action with another action, even if the latter has no more the choice, basically the version given here allows to hide some choices from the hole

% meaning of f, what happens depending on f
% hole function from implem to spec on disjoint holes
\begin{multline*}
	\mathrm{OA}_1 \leq \mathrm{OA}_2 \defnotation \exists f \in J_2 \setminus J_1 \to J_1 \setminus J_2 \\
	\wedge \exists R \in \mpar{S_1 \times S_2} \to \fformulas{E}_1 + \fformulas{E}_2, \exists p, \prel{R}{i_1}{i_2}{p} \wedge \mpar{v_1 \wedge v_2 \Rightarrow p} \\
	\wedge R \text{ f-refinement relation}
\end{multline*}

\begin{multline*}
	R \text{ f-refinement relation} \defnotation \forall \prel{R}{s_1}{s_2}{p}, \\
	\mpar{\begin{array}{l}
		\displaystyle\scalebox{2}{\(\forall\)} \OT{s_2}{s'_2}{\alpha_2\mpar{x_2}}{\mpar{\beta_{2j}\mpar{x_{2j}}}^{j \in J'_2}}{g_2}{\psi_2} \in T_2, \scalebox{2}{\(\exists\)} \mpar{\OT{s_1}{s'_{1y}}{\alpha_{1y}\mpar{x_{1y}}}{\mpar{\beta_{1yj}\mpar{x_{1yj}}}^{j \in J'_{1y}}}{g_{1y}}{\psi_{1y}} \in T_1}^{y \in Y}, \\
		\displaystyle\mpar{\forall y \in Y, \prel{R}{s'_{1y}}{s'_2}{p'_y}} \wedge \mpar{\forall y \in Y, J'_{1y} \cap J_2 = J_1 \cap J'_2} \wedge \mpar{\forall y, f\mpar{J'_2 \setminus J_1} \subseteq J'_{1y} \setminus J_2} \\
		\displaystyle\quad \wedge \mpar{p \wedge g_2 \Rightarrow \operatorname*{\scalebox{2}{\nmm{\bigvee}}}_{y \in Y}
		\mpar{\renewcommand\arraystretch{1.2}\begin{array}{l}
			\displaystyle\mpar{\bigwedge_{j \in J'_1 \cap J'_2} \beta_{2j} = \beta_{1yj} \wedge x_{2j} = x_{1yj}} \\
			\displaystyle\wedge \alpha_2 = \alpha_{1y} \wedge x_2 = x_{1y} \\
			\displaystyle\wedge g_{1y} \wedge p'_y\psubst{\psi_2 + \psi_{1y}}
		\end{array}}}
	\end{array}} \\
	\wedge \mpar{p \wedge \bigvee_\subbox{t_1 \in \mathrm{OT}\mpar{s_1}} \mathit{guard}\mpar{t_1} \Rightarrow \bigvee_\subbox{t_2 \in \mathrm{OT}\mpar{s_2}} \mathit{guard}\mpar{t_2}}
\end{multline*}
% refinement relation definition
% Explain definition, really needed
The objective of the first part of this definition is to be able to simulate \(\mathrm{OA}_2\) in \(\mathrm{OA}_1\) when holes of the same name receive the same closed automaton while other holes receive ``compatible" closed automata.
% safety is no longer trivial, prove the safety
The objective of the other part of this definition is to prevent the appearance of new deadlocks, which should mean with the first property that the compared automaton are deadlock equivalent.
% Expected properties: no new deadlocks, every path can be simulated (safety), composition that do not introduce deadlock is refinement, congruence wrt composition 2-way, most refined are runs

\section{New equivalence relation induced by pre-order}
% FH-behaviourial equivalence if hole functions are not inverse, almost-FH-bisim if function is bijective and FH-bisim if in emptyset -> emptyset

\section{Weak refinement relation}
\begin{multline*}
	\mathrm{OA}_1 \leq_{fH} \mathrm{OA}_2 \defnotation f \in J_2 \setminus J_1 \to J_1 \setminus J_2 \wedge H \subseteq A \\
	\wedge \exists R \in \mpar{S_1 \times S_2} \to \fformulas{E}_1 + \fformulas{E}_2, \prel{R}{i_1}{i_2}{p} \wedge \mpar{v_1 \wedge v_2 \Rightarrow p} \\
	\wedge R \text{ weak f-refinement relation}
\end{multline*}
Often \(H = \mbrc{\tau}\).
% Refinement iff exists weak refinement relation relating initial confs

\begin{multline*}
	R \text{ weak refinement relation} \defnotation \forall \prel{R}{s_1}{s_2}{p}, \\
	\mpar{\begin{array}{l}
		\forall \OT{s_2}{s'_2}{\alpha_2}{\_}{g_2}{\psi_2} \in T_2, \exists \OT{s_1}{s'_{1x}}{\alpha_{1x}}{\_}{g_{1x}}{\psi_{1x}} \in T_1, \mpar{\forall x \in X, \prel{R}{s'_{1x}}{s'_2}{p'_x}} \\
		\wedge \mpar{p \wedge g_2 \Rightarrow \mpar{\bigwedge_{j \in J_1 \cap J_2} \beta_{2j} = \beta_{1jx}} \wedge \alpha_2 = \alpha_{1x} \wedge g_{1x} \wedge p'_x\psubst{\psi_2 + \psi_{1x}}}
	\end{array}} \\
	\wedge \mpar{p \wedge \bigvee_{t_1 \in \mathrm{OT}\mpar{s_1}} \mathit{guard}\mpar{t_1} \Rightarrow \bigvee_{t_2 \in \mathrm{OT}\mpar{s_2}} \mathit{guard}\mpar{t_2}}
\end{multline*}
% weak refinement relation definition
% Expected properties: no new deadlocks and every path can be simulated (safety) and every tau path

\section{Hole equivalence wrt equivalence}
% To define Behavourial equivalence, control

\section{Conclusion}

\end{document}

### 2021-03-22 2021-Refinement/rapport.tex
Refinement v0b
	modified:   rapport.pdf
	modified:   rapport.tex

@@
 \usepackage{unicode-math}
+\usepackage{xcolor}
 \AtBeginDocument{\renewcommand\setminus{\smallsetminus}}
@@
 
-\newcommand\nmm[1]{\(\displaystyle #1\)}
+\newcommand\comment[3]{\colorbox{#1}{#2}\marginpar{#3}}
+\newcommand\Rabea{\comment{yellow}}
+\newcommand\Ludo{\comment{green}}
+\newcommand\Eric{\comment{cyan}}
+\newcommand\Quentin{\comment{pink}}
+
+\newcommand\nmm[1]{\(\displaystyle #1\)} % nmm for Nice Math Mode
 \newcommand\setR{\mathbb{R}}
@@
 \newcommand\defobject{\DOTSB\;{\coloneq}\;}
-\newcommand\nwedge{\DOTSB\;{\wedge}\;}
+\newcommand\nwedge{\DOTSB\;{\wedge}\;} % when you want to force space
 \newcommand\qwedge{\DOTSB\quad{\wedge}\quad}
-\newcommand\sat{{\vdash}}
+\newcommand\sat{{\vdash}} % suppress spaces
 \newcommand\fvars[1]{{\mathit{vars}\mpar{#1}}}
-\newcommand\fterms[1]{{\mathcal{T}\mpar{#1}}}
-\newcommand\fcterms[1]{{\mathcal{T}_{\makebox[1pt][r]{\(\scriptstyle 0\)}}\mpar{#1}}}
-\newcommand\fformulas[1]{{\mathcal{F}\mpar{#1}}}
-\newcommand\fcformulas[1]{{\mathcal{F}_{\makebox[1pt][r]{\(\scriptstyle 0\)}}\mpar{#1}}}
-\newcommand\fvalues[1]{{\mathcal{P}\mpar{#1}}}
-\newcommand\OA[7]{\left<#1,#2,#3,#4, #5,#6,#7\right>}
+\newcommand\fterms[1]{{\mathcal{T}}}
+\newcommand\fcterms[1]{{\mathcal{T}_{\makebox[1pt][r]{\(\scriptstyle 0\)}}}}
+\newcommand\fformulae[1]{{\mathcal{F}}}
+\newcommand\fcformulae[1]{{\mathcal{F}_{\makebox[1pt][r]{\(\scriptstyle 0\)}}}}
+% \newcommand\fterms[1]{{\mathcal{T}\mpar{#1}}}
+% \newcommand\fcterms[1]{{\mathcal{T}_{\makebox[1pt][r]{\(\scriptstyle 0\)}}\mpar{#1}}}
+% \newcommand\fformulae[1]{{\mathcal{F}\mpar{#1}}}
+% \newcommand\fcformulae[1]{{\mathcal{F}_{\makebox[1pt][r]{\(\scriptstyle 0\)}}\mpar{#1}}}
+% \newcommand\fvalues[1]{{\mathcal{P}\mpar{#1}}}
+\newcommand\fvalues[1]{{\mathcal{P}}}
+\newcommand\OA[6]{\left<#1,#2,#3,#4,#5,#6\right>}
 \newcommand\OT[6]{\text{\small\(%
@@
 \begin{defi}[Expression algebra]
-An expression algebra \(E\) is a disjoint union \(E \defobject \mathcal{T} \uplus \mathcal{F}\) where \(\mathcal{T}\) is a term algebra and \(\mathcal{F}\) the formulas over \(\mathcal{T}\).
-
-%TODO: there might be binders in expressions, vars = free veriables, quantifiers are also allowed
-We also define convenience notations \(\fterms{E} \defnotation \mathcal{T}\) and \(\fformulas{E} \defnotation \mathcal{F}\).
+An expression algebra \(E\) is a disjoint union \(E \defobject \mathcal{T} \uplus \mathcal{F}\) where \(\mathcal{T}\) is a term algebra and \(\mathcal{F}\) the formulae over \(\mathcal{T}\).
+% We also define convenience notations \(\fterms{E} \defnotation \mathcal{T}\) and \(\fformulae{E} \defnotation \mathcal{F}\).
 \end{defi}
 The terms algebra is arbitrary.
-The formulas form a propositional logic over terms in \(\mathcal{T}\) and some relations, or equivalently they are first order logic formulas without quantifiers but free variables are allowed.
-An example of term algebra can be Peano integers (zero, variable and successor function), the formulas associated can use the relations equality, \(\mathit{sum}\mpar{a, b, c} \defobject a = b + c\) and \(\mathit{prod}\mpar{a, b, c} \defobject a = b \times c\).
-\begin{defi}[Variables, Closed terms/formulas]
-\(\fvars{e}\) is the set of variables in \(e \in E\).
+The formulae form at least a propositional logic over terms in \(\mathcal{T}\) and some relations, or equivalently they are at least first order logic formulae without quantifiers but with free variables allowed.
+An example of term algebra can be Peano integers (zero, variable and successor function), the formulae associated can use the relations equality, \(\mathit{sum}\mpar{a, b, c} \defobject a = b + c\) and \(\mathit{prod}\mpar{a, b, c} \defobject a = b \times c\).
+\begin{defi}[Free variables, Closed terms/formulae]
+\(\fvars{e}\) is the set of unbound variables in \(e \in E\).
 The closed terms are \(\fcterms{E} \defnotation \mset{t \in \fterms{E}}{\fvars{t} = \emptyset}\); \(\fcterms{E} \subset \fterms{E}\).
-The closed formulas are \(\fcformulas{E} \defnotation \mset{f \in \fformulas{E}}{\fvars{f} = \emptyset}\); \(\fcformulas{E} \subset \fformulas{E}\).
+The closed formulae are \(\fcformulae{E} \defnotation \mset{f \in \fformulae{E}}{\fvars{f} = \emptyset}\); \(\fcformulae{E} \subset \fformulae{E}\).
 \end{defi}
-More generally a closed expression is an expression without variable.
-In a standard context it would be without free variables but here the ``no quantifier" constraint means that there is no such thing as ``bound variables".
+More generally a closed expression is an expression without unbound variable.
+If the expression algebra has no binding construction then closed terms are terms without variables.
 \begin{defi}[Interpretation, Values, Satisfaction, (Parallel) substitution]
@@
 \item The interpretations of closed terms, \(\mdbrk{\_} \in \fcterms{E} \to \fvalues{E}\), with \(\fvalues{E}\) a set of interpreted value of terms;
-\item The satisfaction of closed formulas, \(\sat \in \fcformulas{E} \to \mbrc{0, 1}\);
+\item The satisfaction of closed formulae, \(\sat \subseteq \fcformulae{E} \to \mbrc{0, 1, ?}\);
 \item The substitution in \(e \in E\) of \(x \in \fvars{e}\) by \(t \in \fterms{E}\), \(e\subst{t}{x}\);
 \item The parallel substitution in \(e \in E\) of variables in \(V\) by \(\psi \in \fterms{E}^V\), \(e\psubst{\psi}\).
-% \item The formula interpretation of any variable assignement \(\psi \in \fterms{E}^V\), \nmm{\mdbrk{\psi} \defnotation \bigwedge_{v \in V} v = \psi\mpar{v}}; \(\mdbrk{\psi} \in \fformulas{E}\).
+% \item The formula interpretation of any variable assignement \(\psi \in \fterms{E}^V\), \nmm{\mdbrk{\psi} \defnotation \bigwedge_{v \in V} v = \psi\mpar{v}}; \(\mdbrk{\psi} \in \fformulae{E}\).
 \end{itemize}
@@
 This can be guarded with \(e\subst{t}{x} \in E\) and \(e\psubst{\psi} \in E\) when there is quantification on \(t\) and \(\psi\); in the other cases it is supposed to give a valid expression.
-The interpretation of values and satisfaction are supposed to be decidable.
+The interpretation of values is supposed to be decidable.
+The satisfaction of formulae is not supposed to be decidable, however it is better if it is ;).
 We are not interested in how \(\fvalues{E}\) is defined.
@@
 \begin{itemize}
-\item Let \nmm{f \in \fcformulas{E}}, \nmm{\vdash f_0 \defnotation \sat\mpar{f_0} = 1} and \nmm{\nvdash f_0 \defnotation \sat\mpar{f_0} = 0};
-\item Let \nmm{f \in \fformulas{E}, \sigma \in \fvalues{E}^V}, \\
-	\nmm{\sigma \vdash f \defnotation \exists \varphi \in \fvalues{E}^{\fvars{f} \setminus V}, f\psubst{\sigma \uplus \varphi} \in \fcformulas{E} \nwedge \vdash f\psubst{\sigma \uplus \varphi}}.
+\item Let \nmm{f \in \fcformulae{E}}, \nmm{\vdash f_0 \defnotation \sat\mpar{f_0} = 1} and \nmm{\nvdash f_0 \defnotation \sat\mpar{f_0} = 0};
+\item Let \nmm{f \in \fformulae{E}, \sigma \in \fvalues{E}^V}, \\
+	\nmm{\sigma \vdash f \defnotation \exists \varphi \in \fvalues{E}^{\fvars{f} \setminus V}, f\psubst{\sigma \uplus \varphi} \in \fcformulae{E} \nwedge \vdash f\psubst{\sigma \uplus \varphi}}.
 \end{itemize}
 \end{defi}
-% TODO: redo that explaination
 The first notation is quite classical when satisfaction is defined as a relation rather than a function.
-The second notation means that the disjunction of the right formulas is satisfiable, not necessarily with the same value for a variable name between formulas, for all valid valuation of the left formula.
-\begin{defi}[Formulas combination, Expression algebra combination]
-The propositional logic built without existential quantifiers on top of two propositional logics \(\fformulas{E_1}\) and \(\fformulas{E_2}\) is \(\fformulas{E_1} + \fformulas{E_2}\).
-By extension \(E_1 + E_2 \defnotation \mpar{\fformulas{E_1} + \fformulas{E_2}} \uplus \mpar{\fterms{E_1} \cup \fterms{E_2}}\).
-\end{defi}
+The second notation is the satisfiability of formulae under a (partial) valuation.
+% \begin{defi}[Formulas combination, Expression algebra combination]
+% The propositional logic built without existential quantifiers on top of two propositional logics \(\fformulae{E_1}\) and \(\fformulae{E_2}\) is \(\fformulae{E_1} + \fformulae{E_2}\).
+% By extension \(E_1 + E_2 \defnotation \mpar{\fformulae{E_1} + \fformulae{E_2}} \uplus \mpar{\fterms{E_1} \cup \fterms{E_2}}\).
+% \end{defi}
 
+From there the expression algebra is fixed.
 With these common definitions and notations settled, the objects of interest can now be defined.
 \begin{defi}[Open automaton]
-An open automaton is a tuple \(\OA{S}{i}{E}{V}{\varphi}{J}{T}\) with \(S\) the set of states, \(i \in S\) the initial state, \(E\) an expression algebra, \(V\) the set of variable names unique to this automaton, \(\varphi \in \fvalues{E}^V\) the initial valuation of variables, \(J\) the set of hole names and \(T\) a set of open-transitions.
+An open automaton is a tuple \(\OA{S}{i}{V}{\varphi}{J}{T}\) with \(S\) the set of states, \(i \in S\) the initial state, \(V\) the set of variable names unique to this automaton, \(\varphi \in \fvalues{E}^V\) the initial valuation of variables, \(J\) the set of hole names and \(T\) a set of open-transitions.
 
-\(S, V, J\) are arbitrary sets, only \(J\) is required to be finite.
+\(S, V, J\) are arbitrary sets, \Quentin{only \(J\) is required to be finite.}{Is \(S\) also required to be finite?}
 \end{defi}
-The variable names may clash when considering two automaton, in that case we suppose that we can still distinguish the variables.
+The variable names may clash when considering two automata, in that case we suppose that we can still distinguish the variables.
 All the possible open transitions, from which transitions in \(T\) are selected, are defined below.
 \begin{defi}[Open transition]
-An open transition is a tuple \nmm{\OT{s}{s'}{\alpha\mpar{v_\alpha}}{\mpar{\beta_j\mpar{v_{\beta j}}}^{j \in J'}}{g}{\psi}} with \(s, s' \in S\) the source and target states, \(\alpha \in A\) an action label, \(J' \subseteq J\) the holes involved, \(\beta_j \in A\) the action labels of the holes, \(v_\alpha, v_{\beta j}^{j \in J'}\) fresh distinct variables, \(g \in \fformulas{E}\) the guard and \(\psi \in \fterms{E}^V\) the new value of the variables.
+An open transition is a tuple \nmm{\OT{s}{s'}{\alpha\mpar{v_\alpha}}{\mpar{\beta_j\mpar{v_{\beta j}}}^{j \in J'}}{g}{\psi}} with \(s, s' \in S\) the source and target states, \(\alpha \in A\) an action label, \(J' \subseteq J\) the holes involved, \(\beta_j \in A\) the action labels of the holes, \(v_\alpha, v_{\beta j}^{j \in J'}\) fresh distinct variables, \(g \in \fformulae{E}\) the guard and \(\psi \in \fterms{E}^V\) the new value of the variables.
 
-The set of action labels \(A\) is arbitrary and implicit.
-To simplify formulas, the notations \(\alpha \defnotation \alpha\mpar{v_\alpha}\) and \(\alpha = \beta \defnotation \alpha = \beta \wedge v_\alpha = v_\beta\) will be used.
+\Quentin{The set of action labels \(A\) is arbitrary and implicit.}{For the moment}
+To simplify formulae, the notations \(\alpha \defnotation \alpha\mpar{v_\alpha}\) and \(\alpha = \beta \defnotation \alpha = \beta \wedge v_\alpha = v_\beta\) will be used.
 The guard and new values of the variables can use any defined variable: \nmm{\bigcup_{v \in V} \fvars{\psi\mpar{v}} \cup \fvars{g} \subseteq V \cup \mbrc{v_\alpha} \cup \mset{v_{\beta j}}{j \in J'}}.
@@
 \section{Semantic and composition of Open Automata} % This is taken from 2007.10770.pdf
-% Intro section
-% \begin{defi}[Run of an open autmaton]
-% A run of an open automaton \(\mathrm{OA}_c \defobject \OA{S}{i}{E}{V}{\varphi}{J}{T}\) is a list \(\rho\) of pairs \(\forall k, \rho\mbrk{k} \defobject \mpar{t_k, \nu_k}\) with \(t_k \in T, \nu_k \in \fcterms{E}^\fvars{t_k}\) such that:
-
-% Let \nmm{t_k \defnotation \OTx{k}{}{k}{k}},
-% \begin{itemize}
-% \item \(\forall k, s_k = \choice{i & k = 0 \\ s'_{k-1} & k > 0}\);
-% \item \(\forall k, \sigma\mpar{\rho}\mbrk{k} \defnotation \choice{\varphi & k = 0 \\ \sigma\mpar{\rho}\mbrk{k-1}\psubst{\psi_{k-1}}\psubst{\nu_{k-1}} & k > 0}\), \(\sigma\mpar{\rho}\mbrk{k} \in \fvalues{E}^V\);
-% \item \(\vdash g_k\psubst{\sigma\mpar{\rho}\mbrk{k} \uplus \nu_k}\).
-% \end{itemize}
-% \end{defi}
-% Explain what a run is and what purpose each element serves.
+% TODO: Intro
 When the auomaton is in a state \(s \in S\) with a valuation of its variables \(\sigma \in \fvalues{E}^V\), it cannot perform transitions \nmm{t \defobject \OTg \in T} such that \(\nvdash g\psubst{\sigma}\).
@@
 \begin{defi}[Composition of open automata]
-The composition of \(\mathrm{OA}_c \defobject \OA{S_c}{i_c}{E_c}{V_c}{\varphi_c}{J_c}{T_c}\) in the hole \(k \in J_p\) of \(\mathrm{OA}_p \defobject \OA{S_p}{i_p}{E_p}{V_p}{\varphi_p}{J_p}{T_p}\) is:
+The composition of \(\mathrm{OA}_c \defobject \OA{S_c}{i_c}{V_c}{\varphi_c}{J_c}{T_c}\) in the hole \(k \in J_p\) of \(\mathrm{OA}_p \defobject \OA{S_p}{i_p}{V_p}{\varphi_p}{J_p}{T_p}\) is:
 \begin{align*}
-	\mathrm{OA}_p\subst{\mathrm{OA}_c}{k} \defnotation & \OA{S_p \times S_c}{\mpar{i_p, i_c}}{E_p + E_c}{V_p \uplus V_c}{\varphi_p \uplus \varphi_c}{J_c \uplus J_p \setminus \mbrc{k}}{T} \\
+	\mathrm{OA}_p\subst{\mathrm{OA}_c}{k} \defnotation & \OA{S_p \times S_c}{\mpar{i_p, i_c}}{V_p \uplus V_c}{\varphi_p \uplus \varphi_c}{J_c \uplus J_p \setminus \mbrc{k}}{T} \\
 	\text{With } T \defobject & \mset{\OT{\mpar{s_p, s_c}}{\mpar{s'_p, s'_c}}{\alpha_p}{\beta_j^{j \in J'_c \uplus J'_p \setminus \mbrc{k}}}{g_p \wedge g_c \wedge \alpha_c = \beta_k}{\psi_p \uplus \psi_c}}{\OTx{p}{}{}{p} \in T_p, \OTx{c}{}{}{c} \in T_c} \\
@@
 \begin{description}
-\item[Deadlock preservation:] If \(a \leq b\) then \(a\) does not introduces new deadlocks.
+\item[No deadlock introduction:] If \(a \leq b\) then \(a\) does not introduces new deadlocks.
 \end{description}
-Deadlock preservation conflicts with ``composition is a refinement" by disallowing some unwanted cases where an automaton in a hole cannot produce any action that out-transitions expect.
-In particular filling a hole with the deadlock automaton (one state without out-transitions) is not considered a refinement for a deadlock preserving refinement.
+``No deadlock introduction" conflicts with ``composition is a refinement" by disallowing some unwanted cases where an automaton in a hole cannot produce any action that out-transitions expect.
+In particular filling a hole with the deadlock automaton (one state without out-transitions) is not considered a refinement for a no deadlock introductive refinement.
 This property has another impact which lead to write prerequisites like \(a \leq b \wedge a\mbrk{c} \leq a \implies a\mbrk{c} \leq b\mbrk{c}\) for context equivalence because \(a\mbrk{c} \leq a\) might not be true.
@@
 \begin{description}
-\item[Daisy equivalence:] Filling a hole of \(a\) with a daisy gives \(b\) such that \(a \leq b \wedge b \leq a\), i.e. it is not a strict refinement.
+\item[Daisy equivalence:] Filling a hole of \(a\) with a \Quentin{daisy}{How is it called in english?} gives \(b\) such that \(a \leq b\) and \(b \leq a\), i.e. it is not a strict refinement.
 \end{description}
@@
 The issue especially arise when two independant holes are filled with a daisy, then the other way is simulated by putting back the actions but as a unique hole, effectively merging independant holes.
-% TODO: Expand on why not to do that
+% TODO: Expand on why not to do that, using an example for instance
+\begin{exi}
+\end{exi}
 
@@
 % Caveat (is blablabla a strict refinement) and what we may want (trace/run safety)
+\begin{defi}[Refinement simulation correction] % Correction definition
+\end{defi}
 % Working definition next section
@@
 So looking at restricted cases where holes are related in a specific manner can help understanding the general case.
-For two open automata \(\mathrm{OA}_1 \defobject \OA{S_1}{i_1}{E_1}{J_1}{V_1}{\varphi_1}{T_1}\) and \(\mathrm{OA}_2 \defobject \OA{S_2}{i_2}{E_2}{J_2}{V_2}{\varphi_2}{T_2}\), the following refinement relations are defined.
+For two open automata \(\mathrm{OA}_1 \defobject \OA{S_1}{i_1}{J_1}{V_1}{\varphi_1}{T_1}\) and \(\mathrm{OA}_2 \defobject \OA{S_2}{i_2}{J_2}{V_2}{\varphi_2}{T_2}\), the following refinement relations are defined.
 
-This relation is the basis for all the following ones.
+This relation is the basis for all the other ones.
 It applies on automaton with same holes.
-The goal is to caracterise automata that have a more determined behaviour (more deterministic) without adding deadlocks.
+The goal is to caracterise open automata that have a more determined (more deterministic) behaviour without adding deadlocks.
 \begin{defi}[Hole-identical refinement]
@@
 \begin{multline*}
-	\mathrm{OA}_1 \leq_\equiv \mathrm{OA}_2 \defnotation \exists R \in \mpar{S_1 \times S_2} \to \fformulas{E}_1 + \fformulas{E}_2, \\
-	\mpar{\exists p \in \fformulas{E}_1 + \fformulas{E}_2, \quad \prel{R}{i_1}{i_2}{p} \qwedge \vdash p\psubst{\varphi_1 \uplus \varphi_2}} \\
+%	\mathrm{OA}_1 \leq_= \mathrm{OA}_2 \defnotation \exists R \in \mpar{S_1 \times S_2} \to \fformulae{E}_1 + \fformulae{E}_2, \\
+	\mathrm{OA}_1 \leq_= \mathrm{OA}_2 \defnotation \exists R \in \mpar{S_1 \times S_2} \to \fformulae{E}, \\
+%	\mpar{\exists p \in \fformulae{E}_1 + \fformulae{E}_2, \quad \prel{R}{i_1}{i_2}{p} \qwedge \vdash p\psubst{\varphi_1 \uplus \varphi_2}} \\
+	\mpar{\exists p \in \fformulae{E}, \quad \prel{R}{i_1}{i_2}{p} \qwedge \vdash p\psubst{\varphi_1 \uplus \varphi_2}} \\
 	\wedge R \text{ hole-identical simulation of } \mathrm{OA}_1 \text{ in } \mathrm{OA}_2
@@
 \end{defi}
-As in other simulation-like relations, \(R\) can be seen as a witness of \(\mathrm{OA}_1 \leq_\equiv \mathrm{OA}_2\).
+As in other simulation-like relations, \(R\) can be seen as a witness of \(\mathrm{OA}_1 \leq_= \mathrm{OA}_2\).
 Hence when two open automata are in relation, such a simulation will be called a witness.
 To be a witness the standard requirement is that \(R\) relates initial states, \(R\) is closed under progress and related states are simultaneously final.
+\(R'\) progresses to \(R\) if \(R'\) relates target states of transitions with the same label and with source related states in \(R\).
+Being closed under progress is the same as stating that for all related states, transitions can be matched and target states are also related.
+The latter will be used.
+For a bisimulation transitions are matched one-to-many from each automaton to the other, but for a simulation only one way is used.
 
@@
 	\mpar{\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{} \in T_2, p'_x \in \fformulas{E}_1 + \fformulas{E}_2}^{x \in X}, \\[12pt]
-		\mpar{\forall x \in X, \prel{R}{s'_1}{s'_{2x}}{p'_x}} \wedge \forall \sigma \in \fvalues{E_1}^{V_1 \uplus \fvars{t_1}} \times \fvalues{E_2}^{V_2}, \\[6pt]
-		\quad \sigma \vdash \mpar{p \wedge g_1 \implies \bigvee_{x \in X} \mpar{\alpha_1 = \alpha_{2x} \wedge \bigwedge_{j \in J'} \beta_{1j} = \beta_{2xj} \wedge g_{2x} \wedge p'_x\psubst{\psi_1 \uplus \psi_{2x}}}} \\[12pt]
+		\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{} \in T_2, p'_x \in \fformulae{E}_1 + \fformulae{E}_2}^{x \in X}, \\[12pt]
+%		\mpar{\forall x \in X, \prel{R}{s'_1}{s'_{2x}}{p'_x}} \wedge \forall \sigma \in \fvalues{E_1}^{V_1 \uplus \fvars{t_1}} \times \fvalues{E_2}^{V_2}, \\[6pt]
+		\mpar{\forall x \in X, \prel{R}{s'_1}{s'_{2x}}{p'_x}} \wedge \forall \sigma \in \fvalues{E_1}^{V_1 \uplus \fvars{t_1} \uplus V_2}, \\[6pt]
+		\quad \sigma \sat\mpar{p \wedge g_1 \implies \bigvee_{x \in X} \mpar{\alpha_1 = \alpha_{2x} \wedge \bigwedge_{j \in J'} \beta_{1j} = \beta_{2xj} \wedge g_{2x} \wedge p'_x\psubst{\psi_1 \uplus \psi_{2x}}}} \\[12pt]
 	\end{array}} \\
@@
 \end{defi}
-Being stable wrt.\ progress is the same as stating that for all related states, transitions can be matched and target states are also related (two first lines).
-For a bisimulation transitions are matched one-to-many from each automaton to the other, but for a simulation only one way is used.
-There are some conditions to ensure that transitions are not matched to incompatible ones (3\textsuperscript{rd} line):
+The first two lines describe the fact that transitions can be matched and source and target states are related.
+The 3\textsuperscript{rd} line is the condition to ensure that transitions are not matched to incompatible ones:
 For all variable assignement of the two automata and all hole actions (\(\forall \sigma\) part), assuming that the states were related and the transition in \(\mathrm{OA}_1\) is possible (\(p \wedge g_1\) part) then there is always a transition, not necessarily only one, which can be performed (\(g_{2x}\)), produce the same action (\(\alpha_1 = \alpha_{2x}\)), accept the same action from the holes and satisfy the predicate for relating the target states after variable update (\(p'_x\psubst{\psi_1 \uplus \psi_{2x}}\)).
@@
 The hole-identical part is referring to the fact that holes indicies are the same and identical holes indicies have to perform the same actions.
-On top of that the last line ensures deadlock preservation.
+On top of that the last line ensures no deadlock introduction.
 It can be interpreted ``assuming the predicate holds and there is any possible transition in \(\mathrm{OA}_2\) (= no deadlock), then there must be a possible transition in \(\mathrm{OA}_1\) (= no deadlock)".
 It does not have to ensure that this transition isn't garbage because the first part of the simulation already does it.
-Also if there was a deadlock then there is no transition because no trasition can be simulated in a deadlock, hence deadlock ``preservation" and not ``reduction".
+Also if there was a deadlock then there is no transition because no trasition can be simulated in a deadlock, that's why it is more a deadlock equivalence than a deadlock reduction.
+
+In order to prove that a relation \(R\) is a witness of \(\mathrm{OA}_1 \leq_= \mathrm{OA}_2\) for some automata \(\mathrm{OA}_1\) and \(\mathrm{OA}_2\), there are usually N steps:
+\begin{enumerate}
+\item Proving that \(\exists p \in \fformulae{E}, \quad \prel{R}{i_1}{i_2}{p} \qwedge \vdash p\psubst{\varphi_1 \uplus \varphi_2}\) which is often skipped in concrete examples because it is obvious.
+\item 
+\item 
+\item 
+\end{enumerate}
+% TODO: How to prove a relation is a witness of a refinement
 
@@
 
-% TODO Properties: do not forget to add deadlock equivalence in the 3 theorems
-\begin{thm}[Hole-identical refinement correction] % TODO
-% Let \(\mathrm{OA}_1 \defobject \OA{S_1}{i_1}{E_1}{V_1}{\varphi_1}{J}{T_1}, \mathrm{OA}_2 \defobject \OA{S_2}{i_2}{E_2}{V_2}{\varphi_2}{J}{T_2}\) such that \(\mathrm{OA}_1 \leq_\equiv \mathrm{OA}_2\), for every run \(\) there is a run \(\) such that .
-\end{thm}
-\begin{proof}
-\end{proof}
-% For the completeness there are two case, either the states and value domains of the automata variables are finite or at least one is not.
-% In the first case there is a constructive proof and in the other case a slight modification is required to get the completeness.
-% \begin{thm}[Hole-identical refinement completeness, finite case] % TODO
-% Let \(\mathrm{OA}_1 \defobject \OA{S_1}{i_1}{E_1}{V_1}{\varphi_1}{J}{T_1}, \mathrm{OA}_2 \defobject \OA{S_2}{i_2}{E_2}{V_2}{\varphi_2}{J}{T_2}\) such that \(S_1, S_2, \mdbrk{\fterms{E}_{01}}, \mdbrk{\fterms{E}_{02}}\) are finite and for every run \(\) there is a run \(\) such that , then \(\mathrm{OA}_1 \leq_\equiv \mathrm{OA}_2\).
-% \end{thm}
-% \begin{proof}
-% \end{proof}
-% The non-finite case requires more expressive formulas for the refinement simulation.
-% The way I used to do that is to allow second order formulas with fixed sets and a relation \(y \in Y\).
-\begin{defi}[Second order formulas]
-Let \(E\) be an expression algebra, \(\mathit{SO}\mpar{\fformulas{E}}\) is an extension with pairs of terms, fixed sets and the set membership relation.
-By extension \(\mathit{SO}\mpar{E} \defnotation \fterms{E} \uplus \mathit{SO}\mpar{\fformulas{E}}\).
-\end{defi}
-% \begin{thm}[Hole-identical refinement completeness, general case] % TODO
-% Let \(\mathrm{OA}_1 \defobject \OA{S_1}{i_1}{E_1}{V_1}{\varphi_1}{J}{T_1}, \mathrm{OA}_2 \defobject \OA{S_2}{i_2}{E_2}{V_2}{\varphi_2}{J}{T_2}\) such that \(S_1, S_2, \mdbrk{\fterms{E}_{01}}, \mdbrk{\fterms{E}_{02}}\) are finite and for every run \(\) there is a run \(\) such that , then \(\mathrm{OA}_1 \leq'_\equiv \mathrm{OA}_2\).
-% With \(R \in S_1 \times S_2 \to \mathit{SO}\mpar{E_1 + E_2}\) for the refinement simulation of \(\leq'_\equiv\).
-% \end{thm}
-% \begin{proof}
-% \end{proof}
 \begin{thm} The hole-identical refinement relation is a preorder. \end{thm}
@@
 \item[Transitivity:] Let \(\mathrm{OA}_1, \mathrm{OA}_2, \mathrm{OA}_3\) be open automata with respectively variables in \(V_1, V_2, V_3\).
-	And let \(R_{12}\) be a witness of \(\mathrm{OA}_1 \leq_\equiv \mathrm{OA}_2\) and \(R_{23}\) be a witness of \(\mathrm{OA}_2 \leq_\equiv \mathrm{OA}_3\).
+	And let \(R_{12}\) be a witness of \(\mathrm{OA}_1 \leq_= \mathrm{OA}_2\) and \(R_{23}\) be a witness of \(\mathrm{OA}_2 \leq_= \mathrm{OA}_3\).
 	\begin{align*}
-		R_{13} \defobject & \mset{\mpar{s_1, s_3, \mathit{merge}_{V_1,V_3}\mpar{p_{12}, p_{23}}}}{\prel{R_{12}}{s_1}{s_2}{p_{12}} \wedge \prel{R_{23}}{s_2}{s_3}{p_{23}}} \\
-		\mathit{merge}_{V_1,V_3}\mpar{p_{12}, p_{23}} \defobject & p_{12} \wedge p_{23} % TODO
+		R_{13} \defobject & \mset{\mpar{s_1, s_3, \mathit{merge}_{V_2}\mpar{p_{12}, p_{23}}}}{\prel{R_{12}}{s_1}{s_2}{p_{12}} \wedge \prel{R_{23}}{s_2}{s_3}{p_{23}}} \\
+		\mathit{merge}_{V_2}\mpar{p_{12}, p_{23}} \defobject & p_{12} \wedge p_{23} % TODO HERE
 	\end{align*}
+
+	Now let's prove that \(R_{13}\) is a witness of \(\mathrm{OA}_1 \leq_= \mathrm{OA}_3\):
+	\begin{itemize}
+	\item 
+	\end{itemize}
 \end{description}
+\end{proof}
+% TODO Properties: do not forget to add deadlock equivalence in the 3 theorems
+\begin{thm}[Hole-identical refinement correction]
+% TODO: Préordre, action-refinement possible, pas de nouveau deadlock, pas de nouveau livelock, chaque état (accessible) a son correspondant (simulation)
+\end{thm}
+\begin{proof}
 \end{proof}
@@
 \begin{multline*}
-	\mathrm{OA}_1 \leq_\subseteq \mathrm{OA}_2 \defnotation \exists R \in \mpar{S_1 \times S_2} \to \fformulas{E}_1 + \fformulas{E}_2, \\
-	\mpar{\exists p \in \fformulas{E}_1 + \fformulas{E}_2, \prel{R}{i_1}{i_2}{p} \wedge \vdash p\psubst{\varphi_1 \uplus \varphi_2}} \\
+%	\mathrm{OA}_1 \leq_\subseteq \mathrm{OA}_2 \defnotation \exists R \in \mpar{S_1 \times S_2} \to \fformulae{E}_1 + \fformulae{E}_2, \\
+	\mathrm{OA}_1 \leq_\subseteq \mathrm{OA}_2 \defnotation \exists R \in \mpar{S_1 \times S_2} \to \fformulae{E}, \\
+%	\mpar{\exists p \in \fformulae{E}_1 + \fformulae{E}_2, \prel{R}{i_1}{i_2}{p} \wedge \vdash p\psubst{\varphi_1 \uplus \varphi_2}} \\
+	\mpar{\exists p \in \fformulae{E}, \prel{R}{i_1}{i_2}{p} \wedge \vdash p\psubst{\varphi_1 \uplus \varphi_2}} \\
 	\wedge R \text{ hole-subset simulation of } \mathrm{OA}_1 \text{ in } \mathrm{OA}_2
@@
 	\mpar{\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} \OTx{1}{}{1}{1} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in T_2, p'_x \in \fformulas{E}_1 + \fformulas{E}_2}^{x \in X}, \\[12pt]
-		\mpar{\forall x \in X, \prel{R}{s'_1}{s'_{2x}}{p'_x} \qwedge J'_1 = J'_{2x} \cap J_1} \\
-		\quad \nwedge \mpar{p \wedge g_1} \vdash \mpar{\alpha_1 = \alpha_{2x} \wedge \bigwedge_{j \in J'_1} \beta_{1j} = \beta_{2xj} \wedge g_{2x} \wedge p'_x\psubst{\psi_1 \uplus \psi_{2x}}}^{x \in X} \\[12pt]
+		\bigsymb{\forall} \OTx{1}{}{1}{1} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in T_2, p'_x \in \fformulae{E}_1 + \fformulae{E}_2}^{x \in X}, \\[12pt]
+		\mpar{\forall x \in X, \prel{R}{s'_1}{s'_{2x}}{p'_x} \qwedge J'_1 = J'_{2x} \cap J_1} \wedge \forall \sigma \in \fvalues{E_1}^{V_1 \uplus \fvars{t_1} \uplus V_2}, \\[6pt]
+		\quad \sigma \vdash \mpar{p \wedge g_1 \implies \bigvee_{x \in X} \mpar{\alpha_1 = \alpha_{2x} \wedge \bigwedge_{j \in J'_1} \beta_{1j} = \beta_{2xj} \wedge g_{2x} \wedge p'_x\psubst{\psi_1 \uplus \psi_{2x}}}} \\[12pt]
 	\end{array}} \\
@@
 % TODO: Give an example of what you want to capture BEFORE and after the relation
-% TODO: swap 1 <-> 2
 The difference with the hole-identical simulation is that the holes involved in the matched transitions don't have to be exactly the same anymore.
@@
 \begin{proof}
-% TODO: Proof that it behaves the same as the previous one when holes are identical
+When \(J_1 = J_2\), \(J'_1 = J'_{2x} \cap J_1 \iff J'_1 = J'_{2x} \cap J_2 \iff J'_1 = J'_{2x}\), which is the implicit constraint on hole actions in the hole-identical simulation.
+By that rewriting their definition match.
 \end{proof}
-\begin{prop}[Hole-subset refinement is a pre-order]
-\end{prop}
-\begin{proof}
-\end{proof}
+Let's assume that this relation is also correct, the proof of correctness is given later for a more general refinement relation.
 \begin{thm}[Composition is a refinement]
@@
 
-A relation for which filling holes with one hole open automata is a refinement.
+The goal of the following relation is to capture the case where holes are filled with one hole automata.
+It is supposed to be a relation for which filling holes with one hole automata is a considered refinement.
 \begin{defi}[Hole-matching refinement]
-If \(\card{J_2} = \card{J_1}\) then ``\(\mathrm{OA}_2\) is a hole-matching refinement of \(\mathrm{OA}_1\)" is defined, and its definition is as follows:
+If \(\card{J_1} = \card{J_2}\) then ``\(\mathrm{OA}_1\) is a hole-matching refinement of \(\mathrm{OA}_2\)" is defined, and its definition is as follows:
 \begin{multline*}
-	\mathrm{OA}_2 \leq_\# \mathrm{OA}_1 \defnotation \exists R \in \mpar{S_1 \times S_2} \to \fformulas{E}_1 + \fformulas{E}_2, \quad f \in J_2 \setminus J_1 \to J_1 \setminus J_2, \\
-	\mpar{\exists p \in \fformulas{E}_1 + \fformulas{E}_2, \prel{R}{i_1}{i_2}{p} \wedge \sat\mpar{\mdbrk{\varphi_1} \wedge \mdbrk{\varphi_2} \implies p}} \qwedge f\mpar{J_2 \setminus J_1} = J_1 \setminus J_2 \\
-	\wedge R \text{ hole-f-matching simulation between } \mathrm{OA}_1 \text{ and } \mathrm{OA}_2
+%	\mathrm{OA}_1 \leq_\# \mathrm{OA}_2 \defnotation \exists R \in \mpar{S_1 \times S_2} \to \fformulae{E}_1 + \fformulae{E}_2, \quad f \in J_1 \setminus J_2 \to J_2 \setminus J_1, \\
+	\mathrm{OA}_1 \leq_\# \mathrm{OA}_2 \defnotation \exists R \in \mpar{S_1 \times S_2} \to \fformulae{E}, \quad f \in J_1 \setminus J_2 \to J_2 \setminus J_1, \\
+%	\mpar{\exists p \in \fformulae{E}_1 + \fformulae{E}_2, \prel{R}{i_1}{i_2}{p} \wedge \vdash p\psubst{\varphi_1 \uplus \varphi_2}} \qwedge f\mpar{J_1 \setminus J_2} = J_2 \setminus J_1 \\
+	\mpar{\exists p \in \fformulae{E}, \prel{R}{i_1}{i_2}{p} \wedge \vdash p\psubst{\varphi_1 \uplus \varphi_2}} \qwedge f\mpar{J_1 \setminus J_2} = J_2 \setminus J_1 \\
+	\wedge R \text{ hole-f-matching simulation of } \mathrm{OA}_1 \text{ in } \mathrm{OA}_2
 \end{multline*}
@@
 \begin{defi}[Hole-f-matching simulation]
-\(R\) is a hole-f-matching simulation between \(\mathrm{OA}_1\) and \(\mathrm{OA}_2\) is defined as:
+\(R\) is a hole-f-matching simulation of \(\mathrm{OA}_1\) in \(\mathrm{OA}_2\) is defined as:
 \begin{multline*}
@@
 	\mpar{\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} \OTx{2}{}{2}{2} \in T_2, \bigsymb{\exists} \mpar{\OTx{1}{x}{1x}{1x} \in T_1, p'_x \in \fformulas{E}_1 + \fformulas{E}_2}^{x \in X}, \\[12pt]
-		\mpar{\forall x \in X, \prel{R}{s'_{1x}}{s'_2}{p'_x} \qwedge J'_2 \cap J_1 = J'_{1x} \cap J_2 \qwedge f\mpar{J'_2 \setminus J_1} \subseteq J'_{1x}} \\[4pt]
-		\qquad \nwedge \mpar{p \wedge g_2} \vdash \mpar{\alpha_2 = \alpha_{1x} \wedge \bigwedge_\subbox{j \in J'_2 \cap J_1} \beta_{2j} = \beta_{1xj} \wedge g_{1x} \wedge p'_x\psubst{\psi_2 \uplus \psi_{1x}}}^{x \in X} \\[12pt]
+%		\bigsymb{\forall} \OTx{1}{}{1}{1} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in T_2, p'_x \in \fformulae{E}_1 + \fformulae{E}_2}^{x \in X}, \\[12pt]
+		\bigsymb{\forall} \OTx{1}{}{1}{1} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in T_2, p'_x \in \fformulae{E}}^{x \in X}, \\[12pt]
+		\mpar{\forall x \in X, \prel{R}{s'_1}{s'_{2x}}{p'_x} \qwedge J'_1 \cap J_2 = J'_{2x} \cap J_1 \qwedge f\mpar{J'_1 \setminus J_2} \subseteq J'_{2x}} \\[4pt]
+		\qquad \nwedge \mpar{p \wedge g_1} \vdash \mpar{\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_1 \cap J_2} \beta_{1j} = \beta_{2xj} \wedge g_{2x} \wedge p'_x\psubst{\psi_1 \uplus \psi_{2x}}}^{x \in X} \\[12pt]
 	\end{array}} \\
-	\wedge \sat\mpar{p \wedge \bigvee_\subbox{t_1 \in \mathrm{OT}\mpar{s_1}} \mathit{guard}\mpar{t_1} \implies \bigvee_\subbox{t_2 \in \mathrm{OT}\mpar{s_2}} \mathit{guard}\mpar{t_2}}
+	\wedge \sat\mpar{p \wedge \bigvee_\subbox{t_2 \in \mathrm{OT}\mpar{s_2}} \mathit{guard}\mpar{t_2} \implies \bigvee_\subbox{t_1 \in \mathrm{OT}\mpar{s_1}} \mathit{guard}\mpar{t_1}}
 \end{multline*}
 \end{defi}
-% TODO: Matching a hole data with another hole is done with a_2=a_1x and constraint on respective variables, thus hole data is not uncontrained, same for action label because each transition has only 1 action label
+% TODO HERE: swap 1 <-> 2
+% TODO: Matching a hole data with another hole is done with a_1=a_2x and constraint on respective variables, thus hole data is not uncontrained, same for action label because each transition has only 1 action label
 % TODO: Explain what happens on holes constraints and action constraints
@@
 % hole function from implem to spec on disjoint holes
+\begin{defi}[Open automata refinement]
 \begin{multline*}
 	\mathrm{OA}_1 \leq \mathrm{OA}_2 \defnotation \exists f \in J_2 \setminus J_1 \to J_1 \setminus J_2 \\
-	\wedge \exists R \in \mpar{S_1 \times S_2} \to \fformulas{E}_1 + \fformulas{E}_2, \exists p, \prel{R}{i_1}{i_2}{p} \wedge \mpar{v_1 \wedge v_2 \Rightarrow p} \\
+	\wedge \exists R \in \mpar{S_1 \times S_2} \to \fformulae{E}_1 + \fformulae{E}_2, \exists p, \prel{R}{i_1}{i_2}{p} \wedge \mpar{v_1 \wedge v_2 \Rightarrow p} \\
 	\wedge R \text{ f-refinement relation}
 \end{multline*}
+\end{defi}
 
@@
 	\mathrm{OA}_1 \leq_{fH} \mathrm{OA}_2 \defnotation f \in J_2 \setminus J_1 \to J_1 \setminus J_2 \wedge H \subseteq A \\
-	\wedge \exists R \in \mpar{S_1 \times S_2} \to \fformulas{E}_1 + \fformulas{E}_2, \prel{R}{i_1}{i_2}{p} \wedge \mpar{v_1 \wedge v_2 \Rightarrow p} \\
+	\wedge \exists R \in \mpar{S_1 \times S_2} \to \fformulae{E}_1 + \fformulae{E}_2, \prel{R}{i_1}{i_2}{p} \wedge \mpar{v_1 \wedge v_2 \Rightarrow p} \\
 	\wedge R \text{ weak f-refinement relation}

### 2021-03-26 2021-Refinement/rapport.tex
Refinement v0c

@@
 \usepackage{fontspec}
-\usepackage{geometry}
+\usepackage[hmargin=0.5in,marginparwidth=1.5in,includemp]{geometry}
 \usepackage{amsmath}
@@
 \newtheorem{thm}{Theorem}
+\newtheorem{lem}{Lemma}
 \newtheorem{cor}{Corollary}
@@
 \newcommand\mset[2]{\mbrc{#1\midbar #2}}
-\newcommand\prel[4]{\mbrk{#2\mathrel{#1}#3\midbar #4}}
 \newcommand\subbox[1]{{\makebox[.5\width]{\(\scriptstyle #1\)}}}
-\newcommand\bigsymb[2][\Large]{\text{#1\nmm{#2}}}
+\newcommand\bigsymb[2][\Large]{\text{#1\nmm{#2}}} % DeclareMathDelimiter?
 \newcommand\defnotation{\DOTSB\;{\Colon=}\;}
@@
 \newcommand\qwedge{\DOTSB\quad{\wedge}\quad}
-\newcommand\sat{{\vdash}} % suppress spaces
 \newcommand\fvars[1]{{\mathit{vars}\mpar{#1}}}
-\newcommand\fterms[1]{{\mathcal{T}}}
-\newcommand\fcterms[1]{{\mathcal{T}_{\makebox[1pt][r]{\(\scriptstyle 0\)}}}}
-\newcommand\fformulae[1]{{\mathcal{F}}}
-\newcommand\fcformulae[1]{{\mathcal{F}_{\makebox[1pt][r]{\(\scriptstyle 0\)}}}}
-% \newcommand\fterms[1]{{\mathcal{T}\mpar{#1}}}
-% \newcommand\fcterms[1]{{\mathcal{T}_{\makebox[1pt][r]{\(\scriptstyle 0\)}}\mpar{#1}}}
-% \newcommand\fformulae[1]{{\mathcal{F}\mpar{#1}}}
-% \newcommand\fcformulae[1]{{\mathcal{F}_{\makebox[1pt][r]{\(\scriptstyle 0\)}}\mpar{#1}}}
-% \newcommand\fvalues[1]{{\mathcal{P}\mpar{#1}}}
-\newcommand\fvalues[1]{{\mathcal{P}}}
+\newcommand\terms{{\mathcal{T}}}
+\newcommand\cterms{{\mathcal{T}_{\makebox[1pt][r]{\(\scriptstyle \emptyset\)}}}}
+\newcommand\formulae{{\mathcal{F}}}
+\newcommand\cformulae{{\mathcal{F}_{\makebox[1pt][r]{\(\scriptstyle \emptyset\)}}}}
+\newcommand\values{{\mathcal{P}}}
 \newcommand\OA[6]{\left<#1,#2,#3,#4,#5,#6\right>}
@@
 	\setlength\arraycolsep{2pt}\everymath{\displaystyle}%
+	\renewcommand\arraystretch{1}%
 	\begin{array}{c}%
-	#4,#5,#6 \\\hline
+	#4,#5,#6 \\\noalign{\color{red}\hrule height 1pt}
 	#1\xrightarrow{\raisebox{-1.5pt}[.8\height][0pt]{\makebox[1.4\width]{\(\scriptstyle #3\)}}}#2
@@
 % possible examples for refinement: + <= |, ; <= |
+% transitions between sections
+% Re-read what refinement are used for
 
@@
 \section{Notations}
-Throughout this paper, tuples might be denoted differently depending on what they represent.
-Quantification will be used loosely, any previously defined object in a quantification means that the object is constrained to have that previous value, and any undefined object is defined by the quantifier.
-For instance \(\forall \mpar{x, y} \in \setZ^2, \exists \mpar{x', y} \in \setR^2, P\) means \(\forall \mpar{x, y}, \exists \mpar{x', y'}, y = y' \wedge P\).
+Throughout this paper, tuples might be noted differently depending on what they represent.
+Quantification will be used loosely, any bound name in a quantification means that the object is constrained to have that previous value, and any new name is bound by the quantifier.
+For instance \(\forall \mpar{x, y}, \exists \mpar{x', y}, P\) means \(\forall \mpar{x, y}, \exists \mpar{x', y'}, y = y' \wedge P\).
 
@@
 The latter will only be used when unambiguous; for instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\), but \(\mbrc{\alpha \mapsto 1, \beta \mapsto 2, \gamma \mapsto 3}\) must be represented with one of the two first notation.
-The disjoint union of two maps \(\varphi \in X^I\) and \(\psi \in Y^J\) with \(I \cap J = \emptyset\) is \(\varphi \uplus \psi \in \mpar{X \cup Y}^{I \uplus J}\).
-
-A function with two parameters \(R \in X \times Y \to Z\) might be noted using the relational notation \(\prel{R}{x}{y}{z}\) when it is relevant for noting \(R\mpar{x, y} = z\) or equivalently \(\mpar{x, y, z} \in R\).
+The disjoint union of two maps \(\varphi: I \to X\) and \(\psi: J \to Y\) with \(I \cap J = \emptyset\) is \(\varphi \uplus \psi: \mpar{I \uplus J} \to \mpar{X \cup Y}\).
 
@@
 To define an open automaton we need some preliminary definitions.
-\begin{defi}[Expression algebra]
-An expression algebra \(E\) is a disjoint union \(E \defobject \mathcal{T} \uplus \mathcal{F}\) where \(\mathcal{T}\) is a term algebra and \(\mathcal{F}\) the formulae over \(\mathcal{T}\).
-% We also define convenience notations \(\fterms{E} \defnotation \mathcal{T}\) and \(\fformulae{E} \defnotation \mathcal{F}\).
+\begin{defi}[Expression algebra, Formulae, Terms]
+An expression algebra \(E\) is a disjoint union \(E \defobject \terms \uplus \formulae\) where \(\terms\) is a term algebra and \(\formulae\) the formulae over \(\terms\).
 \end{defi}
 The terms algebra is arbitrary.
-The formulae form at least a propositional logic over terms in \(\mathcal{T}\) and some relations, or equivalently they are at least first order logic formulae without quantifiers but with free variables allowed.
-An example of term algebra can be Peano integers (zero, variable and successor function), the formulae associated can use the relations equality, \(\mathit{sum}\mpar{a, b, c} \defobject a = b + c\) and \(\mathit{prod}\mpar{a, b, c} \defobject a = b \times c\).
-\begin{defi}[Free variables, Closed terms/formulae]
+The formulae form a first order logic over \(\terms\) and some relations.
+An example of term algebra can be Peano integers (zero, variable and successor function), the formulae associated can use equality relation, \(\mathit{sum}\mpar{a, b, c} \defobject a = b + c\) relation and \(\mathit{prod}\mpar{a, b, c} \defobject a = b \times c\) relation.
+
+\begin{defi}[Free variables, Closed terms, Closed formulae]
 \(\fvars{e}\) is the set of unbound variables in \(e \in E\).
-The closed terms are \(\fcterms{E} \defnotation \mset{t \in \fterms{E}}{\fvars{t} = \emptyset}\); \(\fcterms{E} \subset \fterms{E}\).
-The closed formulae are \(\fcformulae{E} \defnotation \mset{f \in \fformulae{E}}{\fvars{f} = \emptyset}\); \(\fcformulae{E} \subset \fformulae{E}\).
+The terms restricted to variables in \(V\) are \(\terms_V \defnotation \mset{t \in \terms}{\fvars{t} = \emptyset}\); \(\terms_V \subset \terms\).
+The formulae restricted to variables in \(V\) are \(\formulae_V \defnotation \mset{f \in \formulae}{\fvars{f} = \emptyset}\); \(\formulae_V \subset \terms\).
+The closed terms are terms restricted to variables in \(\emptyset\), \(\cterms\).
+The closed formulae are formulae restricted to variables in \(\emptyset\), \(\cformulae\).
 \end{defi}
-More generally a closed expression is an expression without unbound variable.
-If the expression algebra has no binding construction then closed terms are terms without variables.
-\begin{defi}[Interpretation, Values, Satisfaction, (Parallel) substitution]
+By extension, expressions restricted to variables and closed expressions are also defined.
+A closed expression is an expression without unbound variable.
+\begin{defi}[Interpretation, Values, Satisfiability, (Parallel) substitution]
 We assume that the following functions are given:
 \begin{itemize}
-\item The interpretations of closed terms, \(\mdbrk{\_} \in \fcterms{E} \to \fvalues{E}\), with \(\fvalues{E}\) a set of interpreted value of terms;
-\item The satisfaction of closed formulae, \(\sat \subseteq \fcformulae{E} \to \mbrc{0, 1, ?}\);
-\item The substitution in \(e \in E\) of \(x \in \fvars{e}\) by \(t \in \fterms{E}\), \(e\subst{t}{x}\);
-\item The parallel substitution in \(e \in E\) of variables in \(V\) by \(\psi \in \fterms{E}^V\), \(e\psubst{\psi}\).
-% \item The formula interpretation of any variable assignement \(\psi \in \fterms{E}^V\), \nmm{\mdbrk{\psi} \defnotation \bigwedge_{v \in V} v = \psi\mpar{v}}; \(\mdbrk{\psi} \in \fformulae{E}\).
+\item The interpretations of closed terms, \(\mdbrk{\_}: \cterms \to \values\), with \(\values\) a set of interpreted value of terms;
+\item The satisfiability relation on closed formulae, \({\vdash} \subseteq \cformulae\) and unsatisfiability relation \({\nvdash} \subseteq \cformulae\);
+\item The substitution in \(e \in E\) of \(x \in \fvars{e}\) by \(t \in \terms\), \(e\subst{t}{x}\);
+\item The parallel substitution in \(e \in E\) of variables in \(V\) by \(\psi: V \to \terms\), \(e\psubst{\psi}\).
 \end{itemize}
 \end{defi}
-The set \(V\) is not required to be a subset of \(\fvars{e}\).
-In the case \(U \defobject V \setminus \fvars{e}, U \neq \emptyset\), the variables in \(U\) are not substituted.
+For the parallel substitution, the set \(V\) is not required to be a subset of \(\fvars{e}\).
+In the case where it is not, the variables in \(V \setminus \fvars{e}\) are not substituted.
 The substitutions might give a nonsensical expression; for instance terms can be integers and pairs with addition, \(\mpar{a + b}\psubst{a \mapsto 7, b \mapsto \mpar{4, 5}}\) is not a valid term.
-This can be guarded with \(e\subst{t}{x} \in E\) and \(e\psubst{\psi} \in E\) when there is quantification on \(t\) and \(\psi\); in the other cases it is supposed to give a valid expression.
+This can be guarded with the atom \(e\subst{t}{x} \in E\) and \(e\psubst{\psi} \in E\) and it will implicitely be the case for instance when there is quantification on \(t\) and \(\psi\) to simplify notations.
+
 The interpretation of values is supposed to be decidable.
-The satisfaction of formulae is not supposed to be decidable, however it is better if it is ;).
-We are not interested in how \(\fvalues{E}\) is defined.
-Whether it is predefined or caracterised by \(\fvalues{E} \defnotation \mdbrk{\fcterms{E}}\) is not the point of this definition.
+The (un)satisfiability of formulae might not be decidable nor complete nor consistent, however we will pretend like they are because these are really hard problems for logicians that we don't want to deal with.\footnote{In practise a term algera with only equality is used, and it is has all these properties.}
+
 A value \(v\) may be used for keeping a variable state, and then injected in terms for substitution.
-While this is correct when \(\fvalues{E} \subseteq \fcterms{E}\), in the other cases this will be used as a shorthand for substitution with any \(t \in \mdbrk{v}^{-1}\).
-\begin{defi}
-The following notations will be used for convenience:
-\begin{itemize}
-\item Let \nmm{f \in \fcformulae{E}}, \nmm{\vdash f_0 \defnotation \sat\mpar{f_0} = 1} and \nmm{\nvdash f_0 \defnotation \sat\mpar{f_0} = 0};
-\item Let \nmm{f \in \fformulae{E}, \sigma \in \fvalues{E}^V}, \\
-	\nmm{\sigma \vdash f \defnotation \exists \varphi \in \fvalues{E}^{\fvars{f} \setminus V}, f\psubst{\sigma \uplus \varphi} \in \fcformulae{E} \nwedge \vdash f\psubst{\sigma \uplus \varphi}}.
-\end{itemize}
-\end{defi}
-The first notation is quite classical when satisfaction is defined as a relation rather than a function.
-The second notation is the satisfiability of formulae under a (partial) valuation.
-% \begin{defi}[Formulas combination, Expression algebra combination]
-% The propositional logic built without existential quantifiers on top of two propositional logics \(\fformulae{E_1}\) and \(\fformulae{E_2}\) is \(\fformulae{E_1} + \fformulae{E_2}\).
-% By extension \(E_1 + E_2 \defnotation \mpar{\fformulae{E_1} + \fformulae{E_2}} \uplus \mpar{\fterms{E_1} \cup \fterms{E_2}}\).
-% \end{defi}
+While this is correct when \(\values \subseteq \cterms\), in the other cases this will be used as a shorthand for substitution with any \(t \in \mdbrk{v}^{-1}\).
+
+We are not interested in how \(\values\) is defined.
+Whether it is predefined or caracterised by \(\values \defnotation \mdbrk{\cterms}\) is not the point of this definition.
+
+The satisfiability relations will be noted using the classical relational notation \(\vdash f \defnotation f \in {\vdash}\) and \(\nvdash f \defnotation f \in {\nvdash}\).
+The usual satisfiability under a partial valuation is noted \nmm{\sigma \vdash f \defnotation \exists \varphi: \mpar{\fvars{f} \setminus V} \to \values, \vdash f\psubst{\sigma \uplus \varphi}} with \(f \in \formulae, \sigma: V \to \values\).
 
@@
 \begin{defi}[Open automaton]
-An open automaton is a tuple \(\OA{S}{i}{V}{\varphi}{J}{T}\) with \(S\) the set of states, \(i \in S\) the initial state, \(V\) the set of variable names unique to this automaton, \(\varphi \in \fvalues{E}^V\) the initial valuation of variables, \(J\) the set of hole names and \(T\) a set of open-transitions.
+An open automaton is a tuple \(\OA{S}{i}{V}{\varphi}{J}{T}\) with \(S\) the set of states, \(i \in S\) the initial state, \(V\) the set of variable names unique to this automaton, \(\varphi: V \to \values\) the initial valuation of variables, \(J\) the set of hole names and \(T\) a set of open-transitions.
 
-\(S, V, J\) are arbitrary sets, \Quentin{only \(J\) is required to be finite.}{Is \(S\) also required to be finite?}
+\(S, V, J\) are arbitrary sets, only \(J\) is required to be finite.
 \end{defi}
-The variable names may clash when considering two automata, in that case we suppose that we can still distinguish the variables.
+The variable names may clash when considering two automata, in that case we suppose that we can still distinguish the variables in the formulas.
 All the possible open transitions, from which transitions in \(T\) are selected, are defined below.
 \begin{defi}[Open transition]
-An open transition is a tuple \nmm{\OT{s}{s'}{\alpha\mpar{v_\alpha}}{\mpar{\beta_j\mpar{v_{\beta j}}}^{j \in J'}}{g}{\psi}} with \(s, s' \in S\) the source and target states, \(\alpha \in A\) an action label, \(J' \subseteq J\) the holes involved, \(\beta_j \in A\) the action labels of the holes, \(v_\alpha, v_{\beta j}^{j \in J'}\) fresh distinct variables, \(g \in \fformulae{E}\) the guard and \(\psi \in \fterms{E}^V\) the new value of the variables.
+An open transition is a tuple \nmm{\OT{s}{s'}{\alpha\mpar{v_\alpha}}{\mpar{\beta_j\mpar{v_{\beta j}}}^{j \in J'}}{g}{\psi}} with \(s, s' \in S\) the source and target states, \(\alpha \in A\) an action label, \(J' \subseteq J\) the holes involved, \(\beta_j \in A\) the action labels of the holes, \(v_\alpha, v_{\beta j}^{j \in J'}\) fresh distinct variables, \(g \in \formulae\) the guard and \(\psi: V \to \terms\) the new value of the variables.
 
-\Quentin{The set of action labels \(A\) is arbitrary and implicit.}{For the moment}
+The set of action labels \(A\) is arbitrary and implicit.
 To simplify formulae, the notations \(\alpha \defnotation \alpha\mpar{v_\alpha}\) and \(\alpha = \beta \defnotation \alpha = \beta \wedge v_\alpha = v_\beta\) will be used.
@@
 % TODO: Intro
-When the auomaton is in a state \(s \in S\) with a valuation of its variables \(\sigma \in \fvalues{E}^V\), it cannot perform transitions \nmm{t \defobject \OTg \in T} such that \(\nvdash g\psubst{\sigma}\).
-After performing the transition and emitting action \(\alpha\), the automaton is in the state \(s'\) with valuation \(\psi\psubst{\sigma \uplus \varphi}\) for some \(\varphi \in \fvalues{E}^\fvars{t}\).
+When the auomaton is in a state \(s \in S\) with a valuation of its variables \(\sigma \in V \to \values\), it cannot perform transitions \nmm{t \defobject \OTg \in T} such that \(\nvdash g\psubst{\sigma}\).
+After performing the transition and emitting action \(\alpha\), the automaton is in the state \(s'\) with valuation \(\psi\psubst{\sigma \uplus \varphi}\) for some \(\varphi: \fvars{t} \to \values\).
 The holes are synchronised using a handshake like mecanism when the transition happens.
-\begin{exi} % Examples
+\begin{exi}
 \end{exi}
@@
 The composition may look like a handshake, with both automata running in parallel (product of states and joint variables) but it is actually not symmetric.
-\begin{exi} % TODO: Examples
+\begin{exi}
 \end{exi}
 
-\section{What is a refinement for Open Automata} % TODO
-% Re-read what refinement are used for
+\section{What is a refinement for Open Automata}
 There are several properties that we may want from a refinement relation.
@@
 For example if we are interested in being able to produce the same sequence of action we may want to use trace set inclusion as a refinement.
-% simulation refinement, hole type refinement, control refinement, (meet semi)lattice refinement (meet=handshake a <= b <=> a = a || b, join=non-det choice), action refinement
+Here the main properties that we want are related to composition and action refinement.
+A suitable kind of refinement relation for this kind of properties is simulation refinement:
+A bisimulation has already been proposed for open automata \marginpar{cite an article here} that is compatible with composition.
+
+% THIS WILL BE RE-WRITTEN LATER
+Other kind of refinement relation that \Quentin{I may explore}{This is a note for possible path, some may be explored, some may not.} are control refinement/hole refinement\footnote{No good formulation atm, the idea is that \(a \leq b \defnotation sth \wedge J_a \setminus J_b \leq_{ctrl} J_b \setminus J_a\), sth is probably a clause to ensure that they behave the same without holes involved.}, (meet semi)lattice refinement\footnote{meet = handshake, \(a \leq b \defnotation a = a || b\) with sync holes, I think this will be equivalent to hole-identical sim, (join=non-det choice?)}, weak-simulation refinement\footnote{Weak variation for each interesting simulation refinement}, composition-correct refinement\footnote{Basically a stricter variant of simulation-refinement where simulation has to take place the other way for some transitions (no different holes?) in order to be correct wrt composition}.
 
@@
 \item[Preorder:] Reflexivity and transitivity;
-\item[Composition is a refinement:] \(\forall a\, b, a\mbrk{b} \leq a\);
-\item[Composition context equivalence:] \(\forall a\, b\, c, a \leq b \wedge a\mbrk{c} \leq a \implies a\mbrk{c} \leq b\mbrk{c}\);
-\item[Composition congruence:] \(\forall a\, b\, c, a \leq b \wedge c\mbrk{a} \leq c \implies c\mbrk{a} \leq c\mbrk{b}\);
-\item[Composition compatibility:] \(\forall a\, b\, c\, d, a \leq b \wedge c \leq d \wedge c\mbrk{a} \leq c \implies c\mbrk{a} \leq d\mbrk{b}\);
-\item[FH-bisimulation compatibility:] \(\forall a\, b\, c, d, a = b \wedge c = d \wedge a \leq c \implies b \leq d\).
+\item[Composition completeness:] \(\forall a\, b, a\mbrk{b} \leq a\);
+\item[Composition correctness:] \(\forall a\, b, a \leq b \implies \exists c, a =_{FH} b\mbrk{c}\);
+\item[Composition context equivalence:] \(\forall a\, b\, c, a \leq b \implies a\mbrk{c} \leq b\mbrk{c}\);
+\item[Composition congruence:] \(\forall a\, b\, c, a \leq b \implies c\mbrk{a} \leq c\mbrk{b}\);
+\item[Composition compatibility:] \(\forall a\, b\, c\, d, a \leq b \wedge c \leq d \implies c\mbrk{a} \leq d\mbrk{b}\);
+\item[FH-bisimulation compatibility:] \(\forall a\, b\, c, d, a =_{FH} b \wedge c =_{FH} d \wedge a \leq c \implies b \leq d\);
+\item[Deadlock reduction:] If \(a \leq b\) then \(a\) does not introduces new deadlocks, noted \(a \sqsubseteq b\) in the following; % TODO: Find a better place to introduce a better definition of deadlock reduction.
+\item[Livelock reduction:] If \(a \leq b\) then \(a\) does not introduces new livelocks, noted \(a \preceq b\) in the following; % TODO: Find a better place to introduce a better definition of livelock reduction.
+\item[\(\tau\)-stuttering:] .% TODO
 \end{description}
-The interesting but not necessary properties are:
+``Deadlock reduction" conflicts with ``composition completeness" by disallowing some unwanted cases where an automaton in a hole cannot produce any action that out-transitions expect.
+% And some other do too
+In particular filling a hole with the deadlock automaton (one state without out-transitions) is not considered a refinement for a no deadlock introductive refinement.
+``Composition completeness" can be modified into ``Deadlock reduction completeness" to be compatible with ``Deadlock reduction": \(\forall a\, b, a\mbrk{b} \sqsubseteq a \implies a\mbrk{b} \leq a\).
+Only the latter will be considered.
+Similar issues arise on other properties and can be fixed by changing the prerequisites to insure that the most deadlock-prone composition of automata is composition complete:
 \begin{description}
-\item[No deadlock introduction:] If \(a \leq b\) then \(a\) does not introduces new deadlocks.
+\item[Composition context equivalence modified:] \(\forall a\, b\, c, a \leq b \wedge a\mbrk{c} \leq a \implies a\mbrk{c} \leq b\mbrk{c}\);
+\item[Composition congruence modified:] \(\forall a\, b\, c, a \leq b \wedge c\mbrk{a} \leq c \implies c\mbrk{a} \leq c\mbrk{b}\);
+\item[Composition compatibility modified:] \(\forall a\, b\, c\, d, a \leq b \wedge c \leq d \wedge c\mbrk{a} \leq c \implies c\mbrk{a} \leq d\mbrk{b}\);
 \end{description}
-``No deadlock introduction" conflicts with ``composition is a refinement" by disallowing some unwanted cases where an automaton in a hole cannot produce any action that out-transitions expect.
-In particular filling a hole with the deadlock automaton (one state without out-transitions) is not considered a refinement for a no deadlock introductive refinement.
-This property has another impact which lead to write prerequisites like \(a \leq b \wedge a\mbrk{c} \leq a \implies a\mbrk{c} \leq b\mbrk{c}\) for context equivalence because \(a\mbrk{c} \leq a\) might not be true.
 
-On the other hand the interesting but actually unwanted properties are:
+On the other hand there is a property that was discussed, that may arise when designing a refinement relation and that is interesting but actually unwanted:
 \begin{description}
-\item[Daisy equivalence:] Filling a hole of \(a\) with a \Quentin{daisy}{How is it called in english?} gives \(b\) such that \(a \leq b\) and \(b \leq a\), i.e. it is not a strict refinement.
+\item[Daisy equivalence:] \(a\mbrk{D} \leq a \wedge a \leq a\mbrk{D}\), where \(D\) is the single state automaton that can produce any action.
 \end{description}
-While daisy equivalence might seem to be a natural property because the daisy being the meaning of a hole, there is actually a difference between the two.
-Daisy equivalence allows to refine by filling a daisy but also by going the other way, that is putting new action restrictions to any transition (and duplicating transitions).
-The issue especially arise when two independant holes are filled with a daisy, then the other way is simulated by putting back the actions but as a unique hole, effectively merging independant holes.
-% TODO: Expand on why not to do that, using an example for instance
+This property state that composing a hole with an automaton which can do anything is not a strict refinement.
+While it might seem to be a natural property because this automaton is the closest to the meaning of a hole in term of automaton, there is actually a difference between the two.
+Daisy equivalence allows to refine by filling a hole but also by going the other way, that is creating a hole name and putting its hole action to any transition (and possibly keeping any of the unmodified transitions).
+The unwanted behaviour arise for instance when two independant holes are filled, then a hole is created and its actions are put where the two other actions were.
+This effectively merges independant holes, or equivalently allows to consider that an automaton can be plug simultaneously into several holes which is not part of the composition semantics.
 \begin{exi}
@@
 
-% refinement on Open Automata
-% Caveat (is blablabla a strict refinement) and what we may want (trace/run safety)
-\begin{defi}[Refinement simulation correction] % Correction definition
+The relations will have to be at least preorders and simulations to be called refinement simulation.
+However a simulation on open automata is more complex than a simulation on a LTS.
+\begin{defi}[Simulation refinement on open automata]
+A relation \(\leq\) is a simulation refinement if it is a preorder and let \(\mathrm{OA}_1 \defobject \OA{S_1}{i_1}{J_1}{V_1}{\varphi_1}{T_1}\) and \(\mathrm{OA}_2 \defobject \OA{S_2}{i_2}{J_2}{V_2}{\varphi_2}{T_2}\), the following holds:
+\begin{multline*}
+	\mathrm{OA}_1 \leq \mathrm{OA}_2 \implies \exists R: \mpar{S_1 \times S_2} \to \formulae_{V_1 \uplus V_2}, \varphi_1 \uplus \varphi_2 \vdash R\mpar{i_1, i_2} \\
+	\wedge \forall \mpar{s_1, s_2} \in S_1 \times S_2, t_1 \defobject \OTx{1}{}{1}{1} \in T_1, \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\
+	\sigma \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \exists \OTx{2}{}{2}{2} \in T_2, \\
+	\sigma \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
+\end{multline*}
+Which means a relation is a simulation refinement if when two automata are related then there must be a relation that relates initial states and valuations and for every pair of state and valuation of the automaton variables that are related, and every possible transitions with valuation of its free variables from the first automaton, there is a possible transition and its valuation such that the produced action matches, the holes actions with same names match and the target states are related.
 \end{defi}
+This is a natural extenion of the notion of simulation on LTS, which is the same definition without valuation and holes (and guards).
+It will serve as a watchdog for any relation that will be defined.
+
 % Working definition next section
 
-\section{Refinement relation}
-The main objective of the refinement relation in this section is to be able to say that a composition is a refinement of the base automaton (\(a\mbrk{b} \leq a\)).
+\section{Preliminary refinement relations}
+The main objective of the refinement relation in this section is to be able to say that a composition of two automata is a refinement of the base automaton (\(a\mbrk{b} \leq a\)).
 However composing an open automaton can give an automaton where not much can be said in terms of hole indicies.
@@
 \begin{defi}[Hole-identical refinement]
-If \(J_1 = J_2\) then ``\(\mathrm{OA}_1\) is a hole-identical refinement of \(\mathrm{OA}_2\)" is defined, and its definition is as follows:
+If \(J_1 = J_2\) then ``\(\mathrm{OA}_1\) is a hole-identical refinement of \(\mathrm{OA}_2\)", noted \(\mathrm{OA}_1 \leq_= \mathrm{OA}_2\), is defined as:
+\[ \exists R: \mpar{S_1 \times S_2} \to \formulae_{V_1 \uplus V_2}, \varphi_1 \uplus \varphi_2 \vdash R\mpar{i_1, i_2} \qwedge R \text{ hole-identical simulation of } \mathrm{OA}_1 \text{ in } \mathrm{OA}_2 \]
+\end{defi}
+As in other simulation-like relations, \(R\) is a witness of \(\mathrm{OA}_1 \leq_= \mathrm{OA}_2\).
+The standard requirements for (bi)simulations are that \(R\) relates initial states, transitions can be matched, and target of matched transitions with related sources are also related.
+For a bisimulation transitions are matched one-to-many from each automaton to the other, but for a simulation only one way is used.
+The definition above requires explicitely that initial states are related, the other requirement are encapsulated in the definition (below) of hole-identical simulation.
+
+The specificities of open automata comes in when relating the (initial) states.
+The relation \(R\) relates \(i_1\) to \(i_2\) under the condition that the curent value of variables satisfies \(R\mpar{i_1, i_2}\).
+If two states \(s_1 \in S_1, s_2 \in S_2\) are not(/never) related then \(\nvdash R\mpar{s_1, s_2}\).
+The predicate \(R\mpar{i_1, i_2}\) is used to take into account the fact that a state is also constituted of the value of the variables.
+This is already used in FH-bisimulation introduced in previous articles about open automata.
+So the meaning of \(\varphi_1 \uplus \varphi_2 \vdash R\mpar{i_1, i_2}\) is that the initial states with the initial valuation are effectively related.
+\begin{defi}[Hole-identical simulation]
+\Quentin{``\(R\) is a hole-identical simulation of \(\mathrm{OA}_1\) in \(\mathrm{OA}_2\)"}{Any idea on how to note that? \(R \vDash \mathrm{OA}_1 \leq_= \mathrm{OA}_2\) for instance.} is defined as:
 \begin{multline*}
-%	\mathrm{OA}_1 \leq_= \mathrm{OA}_2 \defnotation \exists R \in \mpar{S_1 \times S_2} \to \fformulae{E}_1 + \fformulae{E}_2, \\
-	\mathrm{OA}_1 \leq_= \mathrm{OA}_2 \defnotation \exists R \in \mpar{S_1 \times S_2} \to \fformulae{E}, \\
-%	\mpar{\exists p \in \fformulae{E}_1 + \fformulae{E}_2, \quad \prel{R}{i_1}{i_2}{p} \qwedge \vdash p\psubst{\varphi_1 \uplus \varphi_2}} \\
-	\mpar{\exists p \in \fformulae{E}, \quad \prel{R}{i_1}{i_2}{p} \qwedge \vdash p\psubst{\varphi_1 \uplus \varphi_2}} \\
-	\wedge R \text{ hole-identical simulation of } \mathrm{OA}_1 \text{ in } \mathrm{OA}_2
+	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \\
+	\mpar{\everymath{\displaystyle}\begin{array}{l}
+		\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{} \in T_2}^{x \in X}, \\[12pt]
+		\forall \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\
+		\quad \sigma \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_{j \in J'} \beta_{1j} = \beta_{2xj} \\[12pt]
+			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}} \\[12pt]
+	\end{array}} \\
+	\wedge \forall \sigma: \mpar{V_1 \uplus V_2} \to \values, \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \mathrm{OT}\mpar{s_2}} \mathit{guard}\mpar{t_2} \implies \bigvee_\subbox{t_1 \in \mathrm{OT}\mpar{s_1}} \mathit{guard}\mpar{t_1}
 \end{multline*}
 \end{defi}
-As in other simulation-like relations, \(R\) can be seen as a witness of \(\mathrm{OA}_1 \leq_= \mathrm{OA}_2\).
-Hence when two open automata are in relation, such a simulation will be called a witness.
-To be a witness the standard requirement is that \(R\) relates initial states, \(R\) is closed under progress and related states are simultaneously final.
-\(R'\) progresses to \(R\) if \(R'\) relates target states of transitions with the same label and with source related states in \(R\).
-Being closed under progress is the same as stating that for all related states, transitions can be matched and target states are also related.
-The latter will be used.
-For a bisimulation transitions are matched one-to-many from each automaton to the other, but for a simulation only one way is used.
-
-In this model there is no final states so there is no need for that last part.
-The progress closure is stated after as \(R\) being a hole-identical refinement relation.
-The specificities of open automata comes in when relating the (initial) states.
-The relation \(\prel{R}{i_1}{i_2}{p}\) means that \(i_1\) is related to \(i_2\) under the condition that the curent value of variables satisfies \(p\).
-The predicate \(p\) is used to take into account the fact that a state is also constituted of the value of the variables.
-This is already used in FH-bisimulation introduced in previous articles about open automata.
-So it is normal to find right after \(\vdash p\psubst{\varphi_1 \uplus \varphi_2}\) which means that the initial valuation satisfies \(p\).
-\begin{defi}[Hole-identical simulation]
-``\(R\) is a hole-identical simulation of \(\mathrm{OA}_1\) in \(\mathrm{OA}_2\)" is defined as:
-\begin{multline*}
-	\forall \prel{R}{s_1}{s_2}{p}, \\
-	\mpar{\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{} \in T_2, p'_x \in \fformulae{E}_1 + \fformulae{E}_2}^{x \in X}, \\[12pt]
-%		\mpar{\forall x \in X, \prel{R}{s'_1}{s'_{2x}}{p'_x}} \wedge \forall \sigma \in \fvalues{E_1}^{V_1 \uplus \fvars{t_1}} \times \fvalues{E_2}^{V_2}, \\[6pt]
-		\mpar{\forall x \in X, \prel{R}{s'_1}{s'_{2x}}{p'_x}} \wedge \forall \sigma \in \fvalues{E_1}^{V_1 \uplus \fvars{t_1} \uplus V_2}, \\[6pt]
-		\quad \sigma \sat\mpar{p \wedge g_1 \implies \bigvee_{x \in X} \mpar{\alpha_1 = \alpha_{2x} \wedge \bigwedge_{j \in J'} \beta_{1j} = \beta_{2xj} \wedge g_{2x} \wedge p'_x\psubst{\psi_1 \uplus \psi_{2x}}}} \\[12pt]
-	\end{array}} \\
-	\wedge \sat\mpar{p \wedge \bigvee_\subbox{t_2 \in \mathrm{OT}\mpar{s_2}} \mathit{guard}\mpar{t_2} \implies \bigvee_\subbox{t_1 \in \mathrm{OT}\mpar{s_1}} \mathit{guard}\mpar{t_1}}
-\end{multline*}
-\end{defi}
-The first two lines describe the fact that transitions can be matched and source and target states are related.
+The first two lines quantify on source states, transitions (and target states) and source states valuations.
 The 3\textsuperscript{rd} line is the condition to ensure that transitions are not matched to incompatible ones:
-For all variable assignement of the two automata and all hole actions (\(\forall \sigma\) part), assuming that the states were related and the transition in \(\mathrm{OA}_1\) is possible (\(p \wedge g_1\) part) then there is always a transition, not necessarily only one, which can be performed (\(g_{2x}\)), produce the same action (\(\alpha_1 = \alpha_{2x}\)), accept the same action from the holes and satisfy the predicate for relating the target states after variable update (\(p'_x\psubst{\psi_1 \uplus \psi_{2x}}\)).
+For all variable assignement of the two automata and all hole actions (quantification of \(\sigma\)), assuming that the states were related and the transition in \(\mathrm{OA}_1\) is possible (\(R\mpar{s_1, s_2} \wedge g_1\) part) then there is always a transition, not necessarily only one, which can be performed (\(g_{2x}\)), produce the same action (\(\alpha_1 = \alpha_{2x}\)), accept the same action from the holes (\(\beta_{1j} = \beta_{2xj}\)) and satisfy the predicate for relating the target states after variable update (\(R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\)).
 
@@
 It can be interpreted ``assuming the predicate holds and there is any possible transition in \(\mathrm{OA}_2\) (= no deadlock), then there must be a possible transition in \(\mathrm{OA}_1\) (= no deadlock)".
-It does not have to ensure that this transition isn't garbage because the first part of the simulation already does it.
+It does not have to ensure that this transition isn't garbage or that the target states are related because the first part of the simulation already does it.
 Also if there was a deadlock then there is no transition because no trasition can be simulated in a deadlock, that's why it is more a deadlock equivalence than a deadlock reduction.
-
-In order to prove that a relation \(R\) is a witness of \(\mathrm{OA}_1 \leq_= \mathrm{OA}_2\) for some automata \(\mathrm{OA}_1\) and \(\mathrm{OA}_2\), there are usually N steps:
-\begin{enumerate}
-\item Proving that \(\exists p \in \fformulae{E}, \quad \prel{R}{i_1}{i_2}{p} \qwedge \vdash p\psubst{\varphi_1 \uplus \varphi_2}\) which is often skipped in concrete examples because it is obvious.
-\item 
-\item 
-\item 
-\end{enumerate}
-% TODO: How to prove a relation is a witness of a refinement
 
@@
 
+\begin{lem}[Equivalent definition] % equivalence between first part of the definition and simulation refinement
+\begin{gather*}
+\mpar{\everymath{\displaystyle}\begin{array}{l}
+	\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{} \in T_2}^{x \in X}, \\[12pt]
+	\forall \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\
+	\quad \sigma \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+		\alpha_1 = \alpha_{2x} \wedge \bigwedge_{j \in J'} \beta_{1j} = \beta_{2xj} \\[12pt]
+		\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+	\end{array}}
+\end{array}} \\
+\iff \\
+\mpar{\everymath{\displaystyle}\begin{array}{l}
+	\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in T_1, \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\[6pt]
+	\sigma \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \bigsymb{\exists} \OTx{2}{}{2}{2} \in T_2, \\[12pt]
+	\quad \sigma \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
+\end{array}}
+\end{gather*}
+\end{lem}
+The first property is one part of the hole-identical simulation, the second property is the central part of the refinement simulation requirement.
+If we prove the direct way of this equivalence and \(\leq_=\) is a preorder then \(\leq_=\) is a refinement simulation.
+The other way is there because I hope that it will be easier to use this formulation to prove that \(\leq_=\) is a preorder. % Will need to be modified
+One may wonder why it was not used in the definition if it is equivalent.
+The reason is that the formulation used is compatible with SMT solver, the place where it will most probably be used in practise.
+\begin{proof}
+\item[\(\Rightarrow\):] \(\) % TODO HERE
+\item[\(\Leftarrow\):] \(\) % TODO HERE
+\end{proof}
+
 \begin{thm} The hole-identical refinement relation is a preorder. \end{thm}
 \begin{proof}
-\begin{description}
-\item[Reflexivity:] Let \(\mathrm{OA}\) be an open automaton with variables in \(V\).
+\item \emph{Reflexivity:} Let \(\mathrm{OA}\) be an open automaton with variables in \(V\).
 	The automaton variables on the right hand side of the relation will be noted \(v'\) for the equivalent variable \(v \in V\) in the automaton on the left hand side.
@@
 	Checking it is a simple exercise left to the reader in order to understand how the definition works.
-\item[Transitivity:] Let \(\mathrm{OA}_1, \mathrm{OA}_2, \mathrm{OA}_3\) be open automata with respectively variables in \(V_1, V_2, V_3\).
+\item \emph{Transitivity:} Let \(\mathrm{OA}_1, \mathrm{OA}_2, \mathrm{OA}_3\) be open automata with respectively variables in \(V_1, V_2, V_3\) and states \(S_1, S_2, S_3\).
 	And let \(R_{12}\) be a witness of \(\mathrm{OA}_1 \leq_= \mathrm{OA}_2\) and \(R_{23}\) be a witness of \(\mathrm{OA}_2 \leq_= \mathrm{OA}_3\).
-	\begin{align*}
-		R_{13} \defobject & \mset{\mpar{s_1, s_3, \mathit{merge}_{V_2}\mpar{p_{12}, p_{23}}}}{\prel{R_{12}}{s_1}{s_2}{p_{12}} \wedge \prel{R_{23}}{s_2}{s_3}{p_{23}}} \\
-		\mathit{merge}_{V_2}\mpar{p_{12}, p_{23}} \defobject & p_{12} \wedge p_{23} % TODO HERE
-	\end{align*}
+	\[ R_{13}\mpar{s_1, s_3} \defobject \exists V_2, \bigvee_{s_2 \in S_2} R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \]
+	Where \(\exists S, P\), with \(S \defobject \mbrc{v_1, v_2, \cdots, v_\card{S}}\) a finite set of variables, means \(\exists v_1, \exists v_2, \cdots, \exists v_\card{S}, P\).
 
@@
 	\begin{itemize}
-	\item 
+	\item % TODO
 	\end{itemize}
-\end{description}
 \end{proof}
@@
 \begin{defi}[Hole-subset refinement]
-If \(J_1 \subseteq J_2\) then ``\(\mathrm{OA}_1\) is a hole-subset refinement of \(\mathrm{OA}_2\)" is defined, and its definition is as follows:
-\begin{multline*}
-%	\mathrm{OA}_1 \leq_\subseteq \mathrm{OA}_2 \defnotation \exists R \in \mpar{S_1 \times S_2} \to \fformulae{E}_1 + \fformulae{E}_2, \\
-	\mathrm{OA}_1 \leq_\subseteq \mathrm{OA}_2 \defnotation \exists R \in \mpar{S_1 \times S_2} \to \fformulae{E}, \\
-%	\mpar{\exists p \in \fformulae{E}_1 + \fformulae{E}_2, \prel{R}{i_1}{i_2}{p} \wedge \vdash p\psubst{\varphi_1 \uplus \varphi_2}} \\
-	\mpar{\exists p \in \fformulae{E}, \prel{R}{i_1}{i_2}{p} \wedge \vdash p\psubst{\varphi_1 \uplus \varphi_2}} \\
-	\wedge R \text{ hole-subset simulation of } \mathrm{OA}_1 \text{ in } \mathrm{OA}_2
-\end{multline*}
+If \(J_1 \subseteq J_2\) then ``\(\mathrm{OA}_1\) is a hole-subset refinement of \(\mathrm{OA}_2\)", noted \(\mathrm{OA}_1 \leq_\subseteq \mathrm{OA}_2\) is defined as:
+\[ \exists R: \mpar{S_1 \times S_2} \to \formulae_{V_1 \uplus V_2}, \varphi_1 \uplus \varphi_2 \vdash R\mpar{i_1, i_2} \wedge R \text{ hole-subset simulation of } \mathrm{OA}_1 \text{ in } \mathrm{OA}_2 \]
 \end{defi}
@@
 \begin{defi}[Hole-subset simulation]
-\(R\) is a hole-subset simulation of \(\mathrm{OA}_1\) in \(\mathrm{OA}_2\) is defined as:
+``\(R\) is a hole-subset simulation of \(\mathrm{OA}_1\) in \(\mathrm{OA}_2\)" is defined as:
 \begin{multline*}
-	\forall \prel{R}{s_1}{s_2}{p}, \\
-	\mpar{\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} \OTx{1}{}{1}{1} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in T_2, p'_x \in \fformulae{E}_1 + \fformulae{E}_2}^{x \in X}, \\[12pt]
-		\mpar{\forall x \in X, \prel{R}{s'_1}{s'_{2x}}{p'_x} \qwedge J'_1 = J'_{2x} \cap J_1} \wedge \forall \sigma \in \fvalues{E_1}^{V_1 \uplus \fvars{t_1} \uplus V_2}, \\[6pt]
-		\quad \sigma \vdash \mpar{p \wedge g_1 \implies \bigvee_{x \in X} \mpar{\alpha_1 = \alpha_{2x} \wedge \bigwedge_{j \in J'_1} \beta_{1j} = \beta_{2xj} \wedge g_{2x} \wedge p'_x\psubst{\psi_1 \uplus \psi_{2x}}}} \\[12pt]
+	\forall s_1 \in S_1, s_2 \in S_2, \\
+	\mpar{\renewcommand\arraystretch{1.4}\everymath{\displaystyle}\begin{array}{l}
+		\bigsymb{\forall} \OTx{1}{}{1}{1} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in T_2}^{x \in X}, \\
+		\mpar{\forall x \in X, J'_1 = J'_{2x} \cap J_1} \wedge \forall \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\
+		\quad \sigma \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_{j \in J'_1} \beta_{1j} = \beta_{2xj} \\
+			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
 		\end{array}} \\
-	\wedge \sat\mpar{p \wedge \bigvee_\subbox{t_2 \in \mathrm{OT}\mpar{s_2}} \mathit{guard}\mpar{t_2} \implies \bigvee_\subbox{t_1 \in \mathrm{OT}\mpar{s_1}} \mathit{guard}\mpar{t_2}}
+	\end{array}} \\
+	\wedge \forall \sigma: \mpar{V_1 \uplus V_2} \to \values, \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \mathrm{OT}\mpar{s_2}} \mathit{guard}\mpar{t_2} \implies \bigvee_\subbox{t_1 \in \mathrm{OT}\mpar{s_1}} \mathit{guard}\mpar{t_2}
 \end{multline*}
 \end{defi}
-% TODO: Give an example of what you want to capture BEFORE and after the relation
 The difference with the hole-identical simulation is that the holes involved in the matched transitions don't have to be exactly the same anymore.
@@
 What happens on the other holes is unspecified except for the fact that, by being free variables they still need to be valued such that the transition is possible.
+
+\begin{exi} % TODO
+\end{exi}
 
@@
 
+% TODO: Give an example of what you want to capture BEFORE and after the relation
 The goal of the following relation is to capture the case where holes are filled with one hole automata.
@@
 \begin{defi}[Hole-matching refinement]
-If \(\card{J_1} = \card{J_2}\) then ``\(\mathrm{OA}_1\) is a hole-matching refinement of \(\mathrm{OA}_2\)" is defined, and its definition is as follows:
+If \(\card{J_1} = \card{J_2}\) then ``\(\mathrm{OA}_1\) is a hole-matching refinement of \(\mathrm{OA}_2\)", noted \(\mathrm{OA}_1 \leq_\# \mathrm{OA}_2\) is defined as:
 \begin{multline*}
-%	\mathrm{OA}_1 \leq_\# \mathrm{OA}_2 \defnotation \exists R \in \mpar{S_1 \times S_2} \to \fformulae{E}_1 + \fformulae{E}_2, \quad f \in J_1 \setminus J_2 \to J_2 \setminus J_1, \\
-	\mathrm{OA}_1 \leq_\# \mathrm{OA}_2 \defnotation \exists R \in \mpar{S_1 \times S_2} \to \fformulae{E}, \quad f \in J_1 \setminus J_2 \to J_2 \setminus J_1, \\
-%	\mpar{\exists p \in \fformulae{E}_1 + \fformulae{E}_2, \prel{R}{i_1}{i_2}{p} \wedge \vdash p\psubst{\varphi_1 \uplus \varphi_2}} \qwedge f\mpar{J_1 \setminus J_2} = J_2 \setminus J_1 \\
-	\mpar{\exists p \in \fformulae{E}, \prel{R}{i_1}{i_2}{p} \wedge \vdash p\psubst{\varphi_1 \uplus \varphi_2}} \qwedge f\mpar{J_1 \setminus J_2} = J_2 \setminus J_1 \\
+	\exists R: \mpar{S_1 \times S_2} \to \formulae, \quad \exists f: J_1 \setminus J_2 \to J_2 \setminus J_1, \\
+	\varphi_1 \uplus \varphi_2 \vdash R\mpar{i_1, i_2} \qwedge f\mpar{J_1 \setminus J_2} = J_2 \setminus J_1 \\
 	\wedge R \text{ hole-f-matching simulation of } \mathrm{OA}_1 \text{ in } \mathrm{OA}_2
@@
 \begin{multline*}
-	\forall \prel{R}{s_1}{s_2}{p}, \\
-	\mpar{\everymath{\displaystyle}\begin{array}{l}
-%		\bigsymb{\forall} \OTx{1}{}{1}{1} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in T_2, p'_x \in \fformulae{E}_1 + \fformulae{E}_2}^{x \in X}, \\[12pt]
-		\bigsymb{\forall} \OTx{1}{}{1}{1} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in T_2, p'_x \in \fformulae{E}}^{x \in X}, \\[12pt]
-		\mpar{\forall x \in X, \prel{R}{s'_1}{s'_{2x}}{p'_x} \qwedge J'_1 \cap J_2 = J'_{2x} \cap J_1 \qwedge f\mpar{J'_1 \setminus J_2} \subseteq J'_{2x}} \\[4pt]
-		\qquad \nwedge \mpar{p \wedge g_1} \vdash \mpar{\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_1 \cap J_2} \beta_{1j} = \beta_{2xj} \wedge g_{2x} \wedge p'_x\psubst{\psi_1 \uplus \psi_{2x}}}^{x \in X} \\[12pt]
+	\forall s_1 \in S_1, s_2 \in S_2, \\
+	\mpar{\renewcommand\arraystretch{1.4}\everymath{\displaystyle}\begin{array}{l}
+		\bigsymb{\forall} \OTx{1}{}{1}{1} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in T_2}^{x \in X}, \\
+		\mpar{\forall x \in X, J'_1 \cap J_2 = J'_{2x} \cap J_1 \wedge f\mpar{J'_1 \setminus J_2} \subseteq J'_{2x}} \wedge \forall \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\
+		\quad \sigma \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_1 \cap J_2} \beta_{1j} = \beta_{2xj} \\
+			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
 		\end{array}} \\
-	\wedge \sat\mpar{p \wedge \bigvee_\subbox{t_2 \in \mathrm{OT}\mpar{s_2}} \mathit{guard}\mpar{t_2} \implies \bigvee_\subbox{t_1 \in \mathrm{OT}\mpar{s_1}} \mathit{guard}\mpar{t_1}}
+	\end{array}} \\
+	\wedge \forall \sigma: \mpar{V_1 \uplus V_2} \to \values, \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \mathrm{OT}\mpar{s_2}} \mathit{guard}\mpar{t_2} \implies \bigvee_\subbox{t_1 \in \mathrm{OT}\mpar{s_1}} \mathit{guard}\mpar{t_1}
 \end{multline*}
 \end{defi}
-% TODO HERE: swap 1 <-> 2
 % TODO: Matching a hole data with another hole is done with a_1=a_2x and constraint on respective variables, thus hole data is not uncontrained, same for action label because each transition has only 1 action label
@@
 
+\section{Refinement relation for open automata}
 % meaning of f, what happens depending on f
@@
 \begin{defi}[Open automata refinement]
+For any two open automata \(\mathrm{OA}_1 \defobject \OA{S_1}{i_1}{J_1}{V_1}{\varphi_1}{T_1}\) and \(\mathrm{OA}_2 \defobject \OA{S_2}{i_2}{J_2}{V_2}{\varphi_2}{T_2}\), ``\(\mathrm{OA}_1\) is a refinement of \(\mathrm{OA}_2\)", noted \(\mathrm{OA}_1 \leq \mathrm{OA}_2\), is defined as:
 \begin{multline*}
-	\mathrm{OA}_1 \leq \mathrm{OA}_2 \defnotation \exists f \in J_2 \setminus J_1 \to J_1 \setminus J_2 \\
-	\wedge \exists R \in \mpar{S_1 \times S_2} \to \fformulae{E}_1 + \fformulae{E}_2, \exists p, \prel{R}{i_1}{i_2}{p} \wedge \mpar{v_1 \wedge v_2 \Rightarrow p} \\
-	\wedge R \text{ f-refinement relation}
+	\exists R: \mpar{S_1 \times S_2} \to \formulae_{V_1 \uplus V_2}, \exists f: J_1 \setminus J_2 \to J_2 \setminus J_1, \\
+	\varphi_1 \uplus \varphi_2 \vdash R\mpar{i_1, i_2} \wedge R \text{ f simulation of } \mathrm{OA}_1 \text{ in } \mathrm{OA}_2
 \end{multline*}
@@
 
+\begin{defi}[f simulation]
+\(R\) is a f simulation of \(\mathrm{OA}_1\) in \(\mathrm{OA}_2\) is defined as:
 \begin{multline*}
-	R \text{ f-refinement relation} \defnotation \forall \prel{R}{s_1}{s_2}{p}, \\
-	\mpar{\begin{array}{l}
-		\displaystyle\scalebox{2}{\(\forall\)} \OT{s_2}{s'_2}{\alpha_2\mpar{x_2}}{\mpar{\beta_{2j}\mpar{x_{2j}}}^{j \in J'_2}}{g_2}{\psi_2} \in T_2, \scalebox{2}{\(\exists\)} \mpar{\OT{s_1}{s'_{1y}}{\alpha_{1y}\mpar{x_{1y}}}{\mpar{\beta_{1yj}\mpar{x_{1yj}}}^{j \in J'_{1y}}}{g_{1y}}{\psi_{1y}} \in T_1}^{y \in Y}, \\
-		\displaystyle\mpar{\forall y \in Y, \prel{R}{s'_{1y}}{s'_2}{p'_y}} \wedge \mpar{\forall y \in Y, J'_{1y} \cap J_2 = J_1 \cap J'_2} \wedge \mpar{\forall y, f\mpar{J'_2 \setminus J_1} \subseteq J'_{1y} \setminus J_2} \\
-		\displaystyle\quad \wedge \mpar{p \wedge g_2 \Rightarrow \operatorname*{\scalebox{2}{\nmm{\bigvee}}}_{y \in Y}
-		\mpar{\renewcommand\arraystretch{1.2}\begin{array}{l}
-			\displaystyle\mpar{\bigwedge_{j \in J'_1 \cap J'_2} \beta_{2j} = \beta_{1yj} \wedge x_{2j} = x_{1yj}} \\
-			\displaystyle\wedge \alpha_2 = \alpha_{1y} \wedge x_2 = x_{1y} \\
-			\displaystyle\wedge g_{1y} \wedge p'_y\psubst{\psi_2 + \psi_{1y}}
-		\end{array}}}
+	\forall s_1 \in S_1, s_2 \in S_2, \\
+	\mpar{\renewcommand\arraystretch{1.4}\everymath{\displaystyle}\begin{array}{l}
+		\bigsymb{\forall} \OTx{1}{}{1}{1} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in T_1}^{x \in X}, \\
+		\mpar{\forall x \in X, J'_1 \cap J_2 = J'_{2x} \cap J_1 \wedge f\mpar{J'_1 \setminus J_2} \subseteq J'_{2x}} \wedge \forall \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\
+		\quad \sigma \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_1 \cap J_2} \beta_{1j} = \beta_{2xj} \\
+			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
 		\end{array}} \\
-	\wedge \mpar{p \wedge \bigvee_\subbox{t_1 \in \mathrm{OT}\mpar{s_1}} \mathit{guard}\mpar{t_1} \Rightarrow \bigvee_\subbox{t_2 \in \mathrm{OT}\mpar{s_2}} \mathit{guard}\mpar{t_2}}
+	\end{array}} \\
+	\wedge \forall \sigma: \mpar{V_1 \uplus V_2} \to \values, R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \mathrm{OT}\mpar{s_2}} \mathit{guard}\mpar{t_2} \implies \bigvee_\subbox{t_1 \in \mathrm{OT}\mpar{s_1}} \mathit{guard}\mpar{t_1}
 \end{multline*}
+\end{defi}
 % refinement relation definition
 % Explain definition, really needed
-The objective of the first part of this definition is to be able to simulate \(\mathrm{OA}_2\) in \(\mathrm{OA}_1\) when holes of the same name receive the same closed automaton while other holes receive ``compatible" closed automata.
+The objective of the first part of this definition is to be able to simulate \(\mathrm{OA}_1\) in \(\mathrm{OA}_2\) when holes of the same name receive the same closed automaton while other holes receive ``compatible" closed automata.
 % safety is no longer trivial, prove the safety
@@
 
-\section{Weak refinement relation}
-\begin{multline*}
-	\mathrm{OA}_1 \leq_{fH} \mathrm{OA}_2 \defnotation f \in J_2 \setminus J_1 \to J_1 \setminus J_2 \wedge H \subseteq A \\
-	\wedge \exists R \in \mpar{S_1 \times S_2} \to \fformulae{E}_1 + \fformulae{E}_2, \prel{R}{i_1}{i_2}{p} \wedge \mpar{v_1 \wedge v_2 \Rightarrow p} \\
-	\wedge R \text{ weak f-refinement relation}
-\end{multline*}
-Often \(H = \mbrc{\tau}\).
-% Refinement iff exists weak refinement relation relating initial confs
-
-\begin{multline*}
-	R \text{ weak refinement relation} \defnotation \forall \prel{R}{s_1}{s_2}{p}, \\
-	\mpar{\begin{array}{l}
-		\forall \OT{s_2}{s'_2}{\alpha_2}{\_}{g_2}{\psi_2} \in T_2, \exists \OT{s_1}{s'_{1x}}{\alpha_{1x}}{\_}{g_{1x}}{\psi_{1x}} \in T_1, \mpar{\forall x \in X, \prel{R}{s'_{1x}}{s'_2}{p'_x}} \\
-		\wedge \mpar{p \wedge g_2 \Rightarrow \mpar{\bigwedge_{j \in J_1 \cap J_2} \beta_{2j} = \beta_{1jx}} \wedge \alpha_2 = \alpha_{1x} \wedge g_{1x} \wedge p'_x\psubst{\psi_2 + \psi_{1x}}}
-	\end{array}} \\
-	\wedge \mpar{p \wedge \bigvee_{t_1 \in \mathrm{OT}\mpar{s_1}} \mathit{guard}\mpar{t_1} \Rightarrow \bigvee_{t_2 \in \mathrm{OT}\mpar{s_2}} \mathit{guard}\mpar{t_2}}
-\end{multline*}
-% weak refinement relation definition
-% Expected properties: no new deadlocks and every path can be simulated (safety) and every tau path
-
-\section{Hole equivalence wrt equivalence}
-% To define Behavourial equivalence, control
-
 \section{Conclusion}

### 2021-04-06 2021-Refinement/report.tex
Refinement v0something
	new file:   preamble.tex
	renamed:    rapport.pdf -> report.pdf
	renamed:    rapport.tex -> report.tex

--- 2021-03-26 2021-Refinement/rapport.tex
@@
 
-\theoremstyle{plain}
-\newtheorem{thm}{Theorem}
-\newtheorem{lem}{Lemma}
-\newtheorem{cor}{Corollary}
-\newtheorem{prop}{Proposition}
-
-\theoremstyle{definition}
-\newtheorem{defi}{Definition}
-\newtheorem{exi}{Example}
-
-\newcommand\comment[3]{\colorbox{#1}{#2}\marginpar{#3}}
-\newcommand\Rabea{\comment{yellow}}
-\newcommand\Ludo{\comment{green}}
-\newcommand\Eric{\comment{cyan}}
-\newcommand\Quentin{\comment{pink}}
-
-\newcommand\nmm[1]{\(\displaystyle #1\)} % nmm for Nice Math Mode
-\newcommand\setR{\mathbb{R}}
-\newcommand\setZ{\mathbb{Z}}
-\newcommand\setN{\mathbb{N}}
-\newcommand\mpar[1]{{\left(#1\right)}}
-\newcommand\mbrk[1]{{\left[#1\right]}}
-\newcommand\mbrc[1]{{\left\{#1\right\}}}
-\newcommand\mdbrk[1]{\left⟦#1\right⟧}
-\newcommand\card[1]{{\left|#1\right|}}
-\newcommand\psubst[1]{\mbrc{\!\!\mbrc{#1}\!\!}}
-\newcommand\subst[2]{\mbrk{#1\middle/#2}}
-\newcommand\choice[1]{\left\{\everymath{\displaystyle}%
-	\begin{array}{lr}#1\end{array}\right.}
-\newcommand\midbar{\,\middle|\,}
-\newcommand\mset[2]{\mbrc{#1\midbar #2}}
-\newcommand\subbox[1]{{\makebox[.5\width]{\(\scriptstyle #1\)}}}
-\newcommand\bigsymb[2][\Large]{\text{#1\nmm{#2}}} % DeclareMathDelimiter?
-\newcommand\defnotation{\DOTSB\;{\Colon=}\;}
-\newcommand\defobject{\DOTSB\;{\coloneq}\;}
-\newcommand\nwedge{\DOTSB\;{\wedge}\;} % when you want to force space
-\newcommand\qwedge{\DOTSB\quad{\wedge}\quad}
-\newcommand\fvars[1]{{\mathit{vars}\mpar{#1}}}
-\newcommand\terms{{\mathcal{T}}}
-\newcommand\cterms{{\mathcal{T}_{\makebox[1pt][r]{\(\scriptstyle \emptyset\)}}}}
-\newcommand\formulae{{\mathcal{F}}}
-\newcommand\cformulae{{\mathcal{F}_{\makebox[1pt][r]{\(\scriptstyle \emptyset\)}}}}
-\newcommand\values{{\mathcal{P}}}
-\newcommand\OA[6]{\left<#1,#2,#3,#4,#5,#6\right>}
-\newcommand\OT[6]{\text{\small\(%
-	\setlength\arraycolsep{2pt}\everymath{\displaystyle}%
-	\renewcommand\arraystretch{1}%
-	\begin{array}{c}%
-	#4,#5,#6 \\\noalign{\color{red}\hrule height 1pt}
-	#1\xrightarrow{\raisebox{-1.5pt}[.8\height][0pt]{\makebox[1.4\width]{\(\scriptstyle #3\)}}}#2
-	\end{array}\)}}
-\newcommand\OTx[4]{\OT{s_{#1}}{s'_{#1 #2}}{\alpha_{#1 #2}}{\beta_{#3 j}^{j \in J'_{#4}}}{g_{#1 #2}}{\psi_{#1 #2}}}
-\newcommand\OTg{\OTx{}{}{}{}}
+\input{preamble.tex}
 
@@
 The latter will only be used when unambiguous; for instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\), but \(\mbrc{\alpha \mapsto 1, \beta \mapsto 2, \gamma \mapsto 3}\) must be represented with one of the two first notation.
-The disjoint union of two maps \(\varphi: I \to X\) and \(\psi: J \to Y\) with \(I \cap J = \emptyset\) is \(\varphi \uplus \psi: \mpar{I \uplus J} \to \mpar{X \cup Y}\).
+The disjoint union of two maps \(\varphi: I \to X\) and \(\psi: J \to Y\) with \(I \cap J = \emptyset\) is \(\varphi \uplus \psi: I \uplus J \to X \cup Y\).
 
@@
 \begin{defi}[Free variables, Closed terms, Closed formulae]
-\(\fvars{e}\) is the set of unbound variables in \(e \in E\).
-The terms restricted to variables in \(V\) are \(\terms_V \defnotation \mset{t \in \terms}{\fvars{t} = \emptyset}\); \(\terms_V \subset \terms\).
-The formulae restricted to variables in \(V\) are \(\formulae_V \defnotation \mset{f \in \formulae}{\fvars{f} = \emptyset}\); \(\formulae_V \subset \terms\).
-The closed terms are terms restricted to variables in \(\emptyset\), \(\cterms\).
-The closed formulae are formulae restricted to variables in \(\emptyset\), \(\cformulae\).
+\defitem \(\fvars{e}\) is the set of unbound variables in \(e \in E\).
+\defitem The terms restricted to variables in \(V\) are \(\rterms{V} \defnotation \mset{t \in \terms}{\fvars{t} = \emptyset}\); \(\rterms{V} \subset \terms\).
+\defitem The formulae restricted to variables in \(V\) are \(\rformulae{V} \defnotation \mset{f \in \formulae}{\fvars{f} = \emptyset}\); \(\rformulae{V} \subset \terms\).
+\defitem The closed terms are terms restricted to variables in \(\emptyset\), \(\cterms\).
+\defitem The closed formulae are formulae restricted to variables in \(\emptyset\), \(\cformulae\).
 \end{defi}
@@
 \begin{defi}[Interpretation, Values, Satisfiability, (Parallel) substitution]
-We assume that the following functions are given:
-\begin{itemize}
-\item The interpretations of closed terms, \(\mdbrk{\_}: \cterms \to \values\), with \(\values\) a set of interpreted value of terms;
-\item The satisfiability relation on closed formulae, \({\vdash} \subseteq \cformulae\) and unsatisfiability relation \({\nvdash} \subseteq \cformulae\);
-\item The substitution in \(e \in E\) of \(x \in \fvars{e}\) by \(t \in \terms\), \(e\subst{t}{x}\);
-\item The parallel substitution in \(e \in E\) of variables in \(V\) by \(\psi: V \to \terms\), \(e\psubst{\psi}\).
-\end{itemize}
+We assume that the following are given:
+\defitem The values \(\values\), which are interpretations of closed terms;
+\defitem The validity relation on closed formulae, \({\vdash} \subseteq \cformulae\);
+\defitem The substitution in \(e \in E\) of \(x \in \fvars{e}\) by \(t \in \terms\), \(e\subst{t}{x}\);
+\defitem The parallel substitution in \(e \in E\) of variables in \(V\) by \(\psi: V \to \terms\), \(e\psubst{\psi}\).
 \end{defi}
@@
 In the case where it is not, the variables in \(V \setminus \fvars{e}\) are not substituted.
-The substitutions might give a nonsensical expression; for instance terms can be integers and pairs with addition, \(\mpar{a + b}\psubst{a \mapsto 7, b \mapsto \mpar{4, 5}}\) is not a valid term.
-This can be guarded with the atom \(e\subst{t}{x} \in E\) and \(e\psubst{\psi} \in E\) and it will implicitely be the case for instance when there is quantification on \(t\) and \(\psi\) to simplify notations.
+The substitutions might give a nonsensical expression; for instance let the terms be integers and pairs with (pointwise) addition, \(\mpar{a + b}\psubst{a \mapsto 7, b \mapsto \mpar{4, 5}}\) is not a valid term.
+This can be guarded with the atom \(e\subst{t}{x} \in E\) and \(e\psubst{\psi} \in E\) and it will implicitely be the case, for instance when there is quantification on \(t\) and \(\psi\), to simplify notations.
 
-The interpretation of values is supposed to be decidable.
-The (un)satisfiability of formulae might not be decidable nor complete nor consistent, however we will pretend like they are because these are really hard problems for logicians that we don't want to deal with.\footnote{In practise a term algera with only equality is used, and it is has all these properties.}
+The interpretation of terms is supposed to be decidable.
+The validity of formulae might not be decidable nor complete nor consistent, however we will pretend like they are because these are really hard problems for logicians that we don't want to deal with.\footnote{In practise a term algera with only equality is used, and it is has all these properties.}
 
 A value \(v\) may be used for keeping a variable state, and then injected in terms for substitution.
-While this is correct when \(\values \subseteq \cterms\), in the other cases this will be used as a shorthand for substitution with any \(t \in \mdbrk{v}^{-1}\).
+While this is correct when \(\values \subseteq \cterms\), in the other cases this will be used as a shorthand for substitution with any term which can be interpreted as \(v\).
+A quantifier followed by a finite set will be used as a shorthand for the quantification on every variable in the set, for instance \(\forall A, \exists B, P\) with \(A = \mbrc{a_1, \dots, a_\card{A}}, B = \mbrc{b_1, \dots, b_\card{B}}\) means \(\forall a_1, \dots, \forall a_\card{A}, \exists b_1, \dots, \exists b_\card{B}, P\).
 
-We are not interested in how \(\values\) is defined.
-Whether it is predefined or caracterised by \(\values \defnotation \mdbrk{\cterms}\) is not the point of this definition.
-
-The satisfiability relations will be noted using the classical relational notation \(\vdash f \defnotation f \in {\vdash}\) and \(\nvdash f \defnotation f \in {\nvdash}\).
-The usual satisfiability under a partial valuation is noted \nmm{\sigma \vdash f \defnotation \exists \varphi: \mpar{\fvars{f} \setminus V} \to \values, \vdash f\psubst{\sigma \uplus \varphi}} with \(f \in \formulae, \sigma: V \to \values\).
+The validity relations will be noted using the classical relational notation \(\vdash f \defnotation {f \in {\vdash}}\).
+The usual validity of a formula \(f \in \formulae\) is noted \({\vdash f} \defnotation {\vdash \forall \fvars{f}, f}\).
+The usual validity of a formula \(f \in \formulae\) with some fixed valuation \(\sigma: V \to \values\) is noted \({\sigma \vdash f} \defnotation {\vdash \forall\mpar{\fvars{f} \setminus V}, f\psubst{\sigma}}\).
 
@@
 \begin{defi}[Open automaton]
-An open automaton is a tuple \(\OA{S}{i}{V}{\varphi}{J}{T}\) with \(S\) the set of states, \(i \in S\) the initial state, \(V\) the set of variable names unique to this automaton, \(\varphi: V \to \values\) the initial valuation of variables, \(J\) the set of hole names and \(T\) a set of open-transitions.
+A semantic open automaton is a tuple \(\OA{S}{i}{V}{\varphi}{J}{T}\) with \(S\) the set of states, \(i \in S\) the initial state, \(V\) the set of variable names unique to this automaton, \(\varphi: V \to \values\) the initial valuation of variables, \(J\) the set of hole names and \(T\) a set of open-transitions.
 
@@
 \begin{defi}[Open transition]
-An open transition is a tuple \nmm{\OT{s}{s'}{\alpha\mpar{v_\alpha}}{\mpar{\beta_j\mpar{v_{\beta j}}}^{j \in J'}}{g}{\psi}} with \(s, s' \in S\) the source and target states, \(\alpha \in A\) an action label, \(J' \subseteq J\) the holes involved, \(\beta_j \in A\) the action labels of the holes, \(v_\alpha, v_{\beta j}^{j \in J'}\) fresh distinct variables, \(g \in \formulae\) the guard and \(\psi: V \to \terms\) the new value of the variables.
+A semantic open transition is a tuple \nmm{\OT{s}{s'}{\alpha\mpar{v_\alpha}}{\mpar{\beta_j\mpar{v_{\beta j}}}^{j \in J'}}{g}{\psi}} with \(s, s' \in S\) the source and target states, \(\alpha \in \actions\) an action label, \(J' \subseteq J\) the holes involved, \(\beta_j \in \actions\) the action labels of the holes, \(v_\alpha \in \rterms{V}\) the emitted action, \(v_{\beta j}^{j \in J'} \in \rterms{V}\) the hole actions, \(g \in \rformulae{V}\) the guard and \(\psi: V \to \rterms{V}\) the new value of the variables.
+\end{defi}
+The set of action labels \(\actions\) is arbitrary and implicit.
+To simplify formulae, the notations \(\alpha \defnotation \alpha\mpar{v_\alpha}\) and \(\alpha = \beta \defnotation \alpha = \beta \wedge v_\alpha = v_\beta\) will be used.
 
-The set of action labels \(A\) is arbitrary and implicit.
-To simplify formulae, the notations \(\alpha \defnotation \alpha\mpar{v_\alpha}\) and \(\alpha = \beta \defnotation \alpha = \beta \wedge v_\alpha = v_\beta\) will be used.
-The guard and new values of the variables can use any defined variable: \nmm{\bigcup_{v \in V} \fvars{\psi\mpar{v}} \cup \fvars{g} \subseteq V \cup \mbrc{v_\alpha} \cup \mset{v_{\beta j}}{j \in J'}}.
-\end{defi}
 Now we can define some utilitary functions:
-\begin{defi}[Guard, Variables, Out-transition, In-transition]
-\(\mathrm{OT}\mpar{s}\) are called the out-transitions of \(s\) and \(\mathrm{IT}\mpar{s}\) and its in-transitions.
+\begin{defi}[Guard, Out-transition]
+\(\fOT{s}\) are called the out-transitions of \(s\).
 \begin{align*}
-	\mathit{guard}\mpar{\OTg} & \defnotation g & \mathit{}
-	\fvars{\OT{s}{s'}{\alpha\mpar{v_\alpha}}{\mpar{\beta_j\mpar{v_{\beta j}}}^{j \in J'}}{g}{\psi}} & \defnotation \mbrc{v_\alpha} \cup \mset{v_{\beta j}}{j \in J'} \\
-	\mathrm{OT}\mpar{s} & \defnotation \mbrc{\OTg \in T} &
-	\mathrm{IT}\mpar{s'} & \defnotation \mbrc{\OTg \in T}
+	\fguard{\OTg} & \defnotation g &
+	\mathit{target}\mpar{\OTg} & \defnotation s' \\
+	\mathit{Post}\mpar{\OTg} & \defnotation \psi &
+	\fOT{s} & \defnotation \mbrc{\OTg \in T}
 \end{align*}
 \end{defi}
-The intuition of an open automaton is a partially defined LTS with variables, guards on transitions and parametrised actions.
+The intuition of a semantic open automaton is a partially defined LTS with variables, guards on transitions and parametrised actions.
+From this point semantic open automata and open transitions will be called automata and transitions for simplicity.
 
@@
 % TODO: Intro
-When the auomaton is in a state \(s \in S\) with a valuation of its variables \(\sigma \in V \to \values\), it cannot perform transitions \nmm{t \defobject \OTg \in T} such that \(\nvdash g\psubst{\sigma}\).
-After performing the transition and emitting action \(\alpha\), the automaton is in the state \(s'\) with valuation \(\psi\psubst{\sigma \uplus \varphi}\) for some \(\varphi: \fvars{t} \to \values\).
+When the auomaton is in a state \(s \in S\) with a valuation of its variables \(\sigma: V \to \values\), it cannot perform transitions \nmm{\OTg \in T} such that \(\neg g\psubst{\sigma}\).
+After performing the transition and emitting action \(\alpha\), the automaton is in the state \(s'\) with valuation \(\psi\psubst{\sigma}\).
 The holes are synchronised using a handshake like mecanism when the transition happens.
@@
 An open automaton can be partially specified, the partial specification comes from the holes.
-A hole can be filled with an open automaton, this operation is called composition.
+A hole can be filled with an open automaton, this operation is called \Quentin{composition}{Or substitution, or filling, what do you prefer?}.
 \begin{defi}[Composition of open automata]
-The composition of \(\mathrm{OA}_c \defobject \OA{S_c}{i_c}{V_c}{\varphi_c}{J_c}{T_c}\) in the hole \(k \in J_p\) of \(\mathrm{OA}_p \defobject \OA{S_p}{i_p}{V_p}{\varphi_p}{J_p}{T_p}\) is:
+The composition of \(A_c \defobject \OA{S_c}{i_c}{V_c}{\varphi_c}{J_c}{T_c}\) in the hole \(k \in J_p\) of \(A_p \defobject \OA{S_p}{i_p}{V_p}{\varphi_p}{J_p}{T_p}\) is
 \begin{align*}
-	\mathrm{OA}_p\subst{\mathrm{OA}_c}{k} \defnotation & \OA{S_p \times S_c}{\mpar{i_p, i_c}}{V_p \uplus V_c}{\varphi_p \uplus \varphi_c}{J_c \uplus J_p \setminus \mbrc{k}}{T} \\
+	A_p\subst{A_c}{k} \defnotation & \OA{S_p \times S_c}{\mpar{i_p, i_c}}{V_p \uplus V_c}{\varphi_p \uplus \varphi_c}{J_c \uplus J_p \setminus \mbrc{k}}{T} \\
 	\text{With } T \defobject & \mset{\OT{\mpar{s_p, s_c}}{\mpar{s'_p, s'_c}}{\alpha_p}{\beta_j^{j \in J'_c \uplus J'_p \setminus \mbrc{k}}}{g_p \wedge g_c \wedge \alpha_c = \beta_k}{\psi_p \uplus \psi_c}}{\OTx{p}{}{}{p} \in T_p, \OTx{c}{}{}{c} \in T_c} \\
@@
 \end{align*}
-Similarly to expression substitution, the parallel composition is noted \(\mathrm{OA}\psubst{\mathrm{OA}_j^{j \in J}}\).
+Similarly to expression substitution, the parallel composition is noted \(A\psubst{A_j^{j \in J}}\).
 \end{defi}
-The actions emitted when \(\mathrm{OA}_c\) makes a transition is sychronised with the action of the hole \(k\) in transitions of \(\mathrm{OA}_p\) which have it as a hole actions (first transition set, \(\alpha_c = \beta_k\)).
-No transition of \(\mathrm{OA}_c\) is performed when a transition that do not refer to the hole \(k\) is performed in \(\mathrm{OA}_p\) (second transition set, \(k \notin J'\)).
+The actions emitted when \(A_c\) makes a transition is sychronised with the action of the hole \(k\) in transitions of \(A_p\) which have it as a hole actions (first transition set, \(\alpha_c = \beta_k\)).
+No transition of \(A_c\) is performed when a transition that do not refer to the hole \(k\) is performed in \(A_p\) (second transition set, \(k \notin J'\)).
 The composition may look like a handshake, with both automata running in parallel (product of states and joint variables) but it is actually not symmetric.
@@
 The important properties we will consider here are:
+\begin{defi} A relation \(\leq\) is
+\defitem \textbf{reflexive} iff \(\forall a, a \leq a\);
+\defitem \textbf{transitive} iff \(\forall a\, b\, c, a \leq b \wedge b \leq c \implies a \leq c\);
+\defitem \textbf{a preorder} iff it is reflexive and transitive;
+\defitem \textbf{complete w.r.t.\@ composition} iff \(\forall a\, b, a\mbrk{b} \leq a\);
+\defitem \textbf{correct w.r.t.\@ composition} iff \(\forall a\, b, a \leq b \implies \exists c, a \overset{FH}= b\mbrk{c}\);
+\defitem \textbf{context equivalent for composition} iff \(\forall a\, b\, c, a \leq b \implies a\mbrk{c} \leq b\mbrk{c}\);
+\defitem \textbf{congruent for composition} iff \(\forall a\, b\, c, a \leq b \implies c\mbrk{a} \leq c\mbrk{b}\);
+\defitem \textbf{compatible with composition} iff \(\forall a\, b\, c\, d, a \leq b \wedge c \leq d \implies c\mbrk{a} \leq d\mbrk{b}\);
+\defitem \textbf{compatibile with FH-bisimulation} iff \(\forall a\, b\, c, d, a \overset{FH}= b \wedge c \overset{FH}= d \wedge a \leq c \implies b \leq d\).
+\end{defi}
+Reflexivity, transitivity and preorder are classical properties on relations.
+Completeness w.r.t.\@ composition is the fact that every composition is considered a refinement.
+Correctness w.r.t.\@ composition is the fact that a refinement correspond to the left automaton being equivalent to some composition of the right automaton.
+Context equivalence is the refinement being compatible with composition with the same automaton.
+Congruence is the refinement being compatible with being composed in the same automaton.
+Compatibility with composition is the two latter at the same time.
+Finally compatibility with FH-bisimulation is the refinement not being able to distinguish two FH-bisimilar automata.
+
+The relations will have to be at least preorders, simulations and forbid the introduction of deadlocks (state where no transition is possible) to be called refinement simulation.
+On top of that weak refinement are refinement where some actions, typically one named \(\tau\), are considered not observable and do not have to be matched.
+In the weak refinement the relations have to forbid the introduction of livelocks (only a sequence of \(\tau\) possible) and respect \(\tau\)-stuttering \marginpar{cite many things arround here}.
+While being preorder is simple to express for a relation, being a simulation, do not introduce new deadlocks/livelocks and \(\tau\)-stuttering are properties about the states of the related automata, therefore they are more complex to express.
+We will need a preliminary concept before defining them.
+\begin{defi}[Relation under predicate]
+A relation under predicate between states of two automata \(\OA{S_1}{i_1}{J_1}{V_1}{\varphi_1}{T_1}\) and \(\OA{S_2}{i_2}{J_2}{V_2}{\varphi_2}{T_2}\) is a function in \(S_1 \times S_2 \to \rformulae{V_1 \uplus V_2}\).
+Two states \(s_1 \in S_1, s_2 \in S_2\) are related under a valuation \(\sigma: V_1 \uplus V_2 \to \values\) iff \(\sigma \vdash R\mpar{s_1, s_2}\).
+\end{defi}
+Now let's adapt the properties about states of automata to open automata.
+\begin{defi}[Simulation on open automata]
+A relation \(\leq\) is a simulation iff for any two related automata \(\OA{S_1}{i_1}{J_1}{V_1}{\varphi_1}{T_1} \leq \OA{S_2}{i_2}{J_2}{V_2}{\varphi_2}{T_2}\), there is a relation under predicate between their states \(R: S_1 \times S_2 \to \rformulae{V_1 \uplus V_2}\) that satisfies both
+\defitem Initial states are related under initial valuations: \(\varphi_1 \uplus \varphi_2 \vdash R\mpar{i_1, i_2}\);
+\defitem From related states, all out-transitions from \(A_1\) can be simulated in \(A_2\) and their target states are related:
+\begin{multline*}
+	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \sigma: V_1 \uplus V_2 \to \values, \\
+	\bigsymb{\forall} \OTx{1}{}{1}{1} \in T_1, \mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} \OTx{2}{}{2}{2} \in T_2, \\
+	\sigma \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
+\end{multline*}
+\end{defi}
+The last formula means that for every pair of related states under valuation of the automaton variables and every possible transitions (\(\sigma \vdash g_1\)) from the first automaton, there is a possible transition (\(\sigma \vdash g_2\)) such that the produced action matches (\(\alpha_1 = \alpha_2\)), the holes actions from same hole names (\(J'_1 \cap J'_2\)) match (\(\beta_{1j} = \beta_{2j}\)) and the target states are related after variable update.
+This is a natural extenion of the notion of simulation on LTS, which is the same definition without variables and holes and guards.
+It will serve as a watchdog for any relation that will be defined with ``simulation" in its name, except weak-simulation where the transition from the first automaton that produce \(\tau\) actions are excluded.
+
+\begin{defi}[Deadlock reduction]
+A simulation \(\leq\) is deadlock reducing if for all related automata \(A_1 \leq A_2\), where \(A_1 \defobject \OA{S_1}{i_1}{V_1}{\varphi_1}{J_1}{T_1}\) and \(A_2 \defobject \OA{S_2}{i_2}{V_2}{\varphi_2}{J_2}{T_2}\), there is a witness \(R: S_1 \times S_2 \to \rformulae{V_1 \uplus V_2}\) of the fact that it is a simulation that also satisfies
+\begin{multline*}
+	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \sigma: V_1 \uplus V_2 \to \values, \\
+	\mpar{\exists t_2 \in \fOT{s_2}, \sigma \vdash R\mpar{s_1, s_2} \wedge \fguard{t_2}} \implies \bigsymb{\exists} \OTx{2}{}{2}{2} \in T_2, \OTx{1}{}{1}{1} \in T_1, \\
+	\sigma \vdash g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_1 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
+\end{multline*}
+\end{defi}
+This definition extends the requirements of a simulation by requiring from the relation that on related states, if there is at least one possible transition in the second automata then there must be a matching possible transition in the first.
+This requirement effectively prevents the presence of deadlock state in the first automaton if there is a related non-deadlock state in the second.
+
+% TODO LATER: livelock and tau-stuttering
+% \item[Livelock reduction:] If \(a \leq b\) then \(a\) does not introduces new livelocks, noted \(a \preceq b\) in the following; % TODO: Find a better place to introduce a better definition of livelock reduction.
+% \defitem \textbf{\(\tau\)-stuttering} iff . % TODO
+
+On the other hand there is a property that we considered for some time, that may arise when designing a refinement relation and that is interesting but actually unwanted:
 \begin{description}
-\item[Reflexivity:] \(\forall a, a \leq a\);
-\item[Transitivity:] \(\forall a\, b\, c, a \leq b \wedge b \leq c \implies a \leq c\);
-\item[Preorder:] Reflexivity and transitivity;
-\item[Composition completeness:] \(\forall a\, b, a\mbrk{b} \leq a\);
-\item[Composition correctness:] \(\forall a\, b, a \leq b \implies \exists c, a =_{FH} b\mbrk{c}\);
-\item[Composition context equivalence:] \(\forall a\, b\, c, a \leq b \implies a\mbrk{c} \leq b\mbrk{c}\);
-\item[Composition congruence:] \(\forall a\, b\, c, a \leq b \implies c\mbrk{a} \leq c\mbrk{b}\);
-\item[Composition compatibility:] \(\forall a\, b\, c\, d, a \leq b \wedge c \leq d \implies c\mbrk{a} \leq d\mbrk{b}\);
-\item[FH-bisimulation compatibility:] \(\forall a\, b\, c, d, a =_{FH} b \wedge c =_{FH} d \wedge a \leq c \implies b \leq d\);
-\item[Deadlock reduction:] If \(a \leq b\) then \(a\) does not introduces new deadlocks, noted \(a \sqsubseteq b\) in the following; % TODO: Find a better place to introduce a better definition of deadlock reduction.
-\item[Livelock reduction:] If \(a \leq b\) then \(a\) does not introduces new livelocks, noted \(a \preceq b\) in the following; % TODO: Find a better place to introduce a better definition of livelock reduction.
-\item[\(\tau\)-stuttering:] .% TODO
+\item[Daisy equivalence:] \(a\mbrk{D} \leq a \wedge a \leq a\mbrk{D}\), where \(D\) is the single state automaton that can produce any action. % TODO: Find another name
 \end{description}
-``Deadlock reduction" conflicts with ``composition completeness" by disallowing some unwanted cases where an automaton in a hole cannot produce any action that out-transitions expect.
-% And some other do too
-In particular filling a hole with the deadlock automaton (one state without out-transitions) is not considered a refinement for a no deadlock introductive refinement.
+This property state that composing a hole with an automaton which can do anything is not a strict refinement.
+While it might seem to be a natural property because this automaton is the closest to the meaning of a hole in term of automaton, there is actually a difference between the two.
+Daisy equivalence allows to refine by filling a hole but also by going the other way, that is creating a hole name and putting its hole action to any transition (and possibly keeping any of the unmodified transitions).
+The unwanted behaviour arise for instance when two independant holes are filled, then a hole is created and its actions are put where the two other actions were.
+This effectively merges independant holes, or equivalently allows to consider that an automaton can be plug simultaneously into several holes which is not part of the composition semantics.
+\begin{exi}
+\end{exi}
+
+``Deadlock reduction" conflicts with ``composition completeness" by disallowing some unwanted cases where an automaton in a hole cannot produce any action that any out-transitions expects.
+In particular filling a hole with the deadlock automaton (only one state without out-transitions) is not considered a refinement for a no deadlock reducing simulation refinement.
+A way to solve this issue is to caracterise a correct composition that will be used instead of the composition introduced earlier.
+\begin{defi}[Correct composition]
+The composition \(A_p\subst{A_c}{k} \defobject \OA{S}{i}{V}{\varphi}{J}{T}\) where \(A_c \defobject \OA{S_c}{i_c}{V_c}{\varphi_c}{J_c}{T_c}\), \(k \in J_p\) and \(A_p \defobject \OA{S_p}{i_p}{V_p}{\varphi_p}{J_p}{T_p}\), is a correct composition if there is a predicate on its states \(p: S \to \rformulae{V}\) that satisfies both
+\defitem Being valid on initial states under initial valuation: \(\varphi \vdash p\mpar{i}\)
+\defitem From states where the predicate is valid, if a transition was possible in \(A_p\) then a transition is possible in \(A\) and the predicate holds in the target state:
+\[ \forall s \in S, \sigma: V \to \values, \mpar{\exists t_p \in \fOT{\pi_{S_p}\mpar{s}}, \sigma \vdash p\mpar{s} \wedge \fguard{t_p}} \implies \bigsymb{\exists} \OTg \in T, \sigma \vdash g \wedge p\mpar{s'}\psubst{\psi} \]
+\end{defi}
+For the reader not used to simulations and bisimulations, this definition with a witness can seem strange.
+In fact the role of the witness is to caracterise reachable configurations without having to caracterise the fact that the state and valuation are the result of a valid path in an automaton.
+
+When expanding the aliases \(S, i, V\) in the definition, and remarking that the last existential quantifier can be unfolded into a transition in \(A\) and one in \(A_p\) with the added condition that they match, the definition become mildly similar with the deadlock reduction one.
+It is not a coincidence because their goal is to caracterise the same kind of compatibility between automata.
+Actually it is possible to simplify both definition and make them shockingly similar.
+
+\begin{lem}
+The formula in the definition of deadlock reduction is equivalent to the following:
+\[ \forall \mpar{s_1, s_2} \in S_1 \times S_2, \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \]
+\end{lem}
+\begin{proof} Let \(R\) be a witness of the simulation \(A_1 \leq A_2\).
+\item[\(\implies\):] If \(R\) satisfies the deadlock reduction definition, let \(\mpar{s_1, s_2} \in S_1 \times S_2\).
+	The free variables of the equivalent formula are all in \(V_1 \uplus V_2\) so let \(\sigma: V_1 \uplus V_2 \to \values\) be such that
+	\[ \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \]
+	We can decompose it by admitting the left part of the implication then decomposing the big disjunction to get \(\sigma \vdash R\mpar{s_1, s_2}\) as \hyp{p} and \(t_2 \in \fOT{s_2}\) such that \hyp{g2}: \(\sigma \vdash \fguard{t_2}\).
+	We are left to prove \[ \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{G1} \]
+	To do that we will use the fact that \(R\) satisfies the deadlock reduction definition with the current value of \(s_1, s_2, \sigma\).
+	Now we additionally need to prove \goal{G2}: \(\exists t_2 \in \fOT{s_2}, \sigma \vdash R\mpar{s_1, s_2} \wedge \fguard{t_2}\) before getting hypothesis \hyp{E}:
+	\[ \bigsymb{\exists} \OTx{2}{}{2}{2} \in T_2, \OTx{1}{}{1}{1} \in T_1, \sigma \vdash g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_1 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \]
+	The witness of \goal{G2} is \(t_2\) obtained previously in the big disjunction, and \(\sigma \vdash R\mpar{s_1, s_2} \wedge \fguard{t_2}\) is proved by combining \hyp{p} and \hyp{g2}.
+	Now we can decompose \hyp{E} to get \(t_1 \in T_1\), which we know is also in \(\fOT{s_1}\), a transition that we won't use and \(\sigma \vdash \fguard{t_1}\) which is what we needed to prove the branch \(t_1\) of \goal{G1}.
+\item[\(\impliedby\):] If \(R\) satisfies the equivalent formula, let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \(\sigma: V_1 \uplus V_2 \to \values\).
+	Let admit that there is a transition \(t_2 \in T_2\) such that \hyp{g2}: \(\sigma \vdash R\mpar{s_1, s_2} \wedge \fguard{t_2}\).
+	We need to prove \goal{G1}:
+	\[ \bigsymb{\exists} \OTx{2}{}{2}{2} \in T_2, \OTx{1}{}{1}{1} \in T_1, \sigma \vdash g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_1 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \]
+	We use the fact that \(R\) satisfies the equivalent formula with the current value of \(s_1, s_2\) and \(\sigma\) to get
+	\[ \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \]
+	As this formula is true for all values of each free variable, it is especially true when valuated with \(\sigma\).
+	We know that \(t_2 \in \fOT{s_2}\) so \hyp{g2} proves the left part of that implication and we immediately decompose the right side to get \(t_1 \in \fOT{s_1}\) and \hyp{g1}: \(\fguard{t_1}\).
+
+	We cannot yet prove \goal{G1} because at this point we don't know whether \(t_2\) and \(t_1\) do match.
+	In order to get a matching \(t_2\) we use the fact that \(R\) is also witness of the simulation \(A_1 \leq A_2\) with the current value of \(s_1, s_2, \sigma\) and \(t_1\) as \hyp{sim}:
+	\[ \mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} \OTx{2}{}{2}{2} \in T_2, \sigma \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \]
+	The left part of the implication is the left side of \hyp{g2} so we get \(t'_2 \in T_2\) and what's after as the hypothesis \hyp{t}.
+	The witnesses for \goal{G1} are \(t'_2\) and \(t_1\), and the rest is proved with a combination of \hyp{t} and \hyp{g1}.
+\end{proof}
+
+\begin{lem}
+The second part of the formula in the definition of correct composition is equivalent to the following:
+\[ \forall s \in S, \vdash p\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \mpar{\fguard{t} \wedge p\mpar{\mathit{target}\mpar{t}}\psubst{\mathit{Post}\mpar{t}}} \]
+\end{lem}
+\begin{proof}
+% TODO HERE
+\end{proof}
+From this point and in the previous definitions, composition will only refer to correct composition.
+
+% TODO: Some equivalences
 ``Composition completeness" can be modified into ``Deadlock reduction completeness" to be compatible with ``Deadlock reduction": \(\forall a\, b, a\mbrk{b} \sqsubseteq a \implies a\mbrk{b} \leq a\).
@@
 
-On the other hand there is a property that was discussed, that may arise when designing a refinement relation and that is interesting but actually unwanted:
-\begin{description}
-\item[Daisy equivalence:] \(a\mbrk{D} \leq a \wedge a \leq a\mbrk{D}\), where \(D\) is the single state automaton that can produce any action.
-\end{description}
-This property state that composing a hole with an automaton which can do anything is not a strict refinement.
-While it might seem to be a natural property because this automaton is the closest to the meaning of a hole in term of automaton, there is actually a difference between the two.
-Daisy equivalence allows to refine by filling a hole but also by going the other way, that is creating a hole name and putting its hole action to any transition (and possibly keeping any of the unmodified transitions).
-The unwanted behaviour arise for instance when two independant holes are filled, then a hole is created and its actions are put where the two other actions were.
-This effectively merges independant holes, or equivalently allows to consider that an automaton can be plug simultaneously into several holes which is not part of the composition semantics.
-\begin{exi}
-\end{exi}
-
-The relations will have to be at least preorders and simulations to be called refinement simulation.
-However a simulation on open automata is more complex than a simulation on a LTS.
-\begin{defi}[Simulation refinement on open automata]
-A relation \(\leq\) is a simulation refinement if it is a preorder and let \(\mathrm{OA}_1 \defobject \OA{S_1}{i_1}{J_1}{V_1}{\varphi_1}{T_1}\) and \(\mathrm{OA}_2 \defobject \OA{S_2}{i_2}{J_2}{V_2}{\varphi_2}{T_2}\), the following holds:
-\begin{multline*}
-	\mathrm{OA}_1 \leq \mathrm{OA}_2 \implies \exists R: \mpar{S_1 \times S_2} \to \formulae_{V_1 \uplus V_2}, \varphi_1 \uplus \varphi_2 \vdash R\mpar{i_1, i_2} \\
-	\wedge \forall \mpar{s_1, s_2} \in S_1 \times S_2, t_1 \defobject \OTx{1}{}{1}{1} \in T_1, \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\
-	\sigma \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \exists \OTx{2}{}{2}{2} \in T_2, \\
-	\sigma \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
-\end{multline*}
-Which means a relation is a simulation refinement if when two automata are related then there must be a relation that relates initial states and valuations and for every pair of state and valuation of the automaton variables that are related, and every possible transitions with valuation of its free variables from the first automaton, there is a possible transition and its valuation such that the produced action matches, the holes actions with same names match and the target states are related.
-\end{defi}
-This is a natural extenion of the notion of simulation on LTS, which is the same definition without valuation and holes (and guards).
-It will serve as a watchdog for any relation that will be defined.
-
-% Working definition next section
+% Transition: Working definitions next section
 
@@
 So looking at restricted cases where holes are related in a specific manner can help understanding the general case.
-For two open automata \(\mathrm{OA}_1 \defobject \OA{S_1}{i_1}{J_1}{V_1}{\varphi_1}{T_1}\) and \(\mathrm{OA}_2 \defobject \OA{S_2}{i_2}{J_2}{V_2}{\varphi_2}{T_2}\), the following refinement relations are defined.
+For two open automata \(A_1 \defobject \OA{S_1}{i_1}{J_1}{V_1}{\varphi_1}{T_1}\) and \(A_2 \defobject \OA{S_2}{i_2}{J_2}{V_2}{\varphi_2}{T_2}\), the following refinement relations are defined.
 
@@
 \begin{defi}[Hole-identical refinement]
-If \(J_1 = J_2\) then ``\(\mathrm{OA}_1\) is a hole-identical refinement of \(\mathrm{OA}_2\)", noted \(\mathrm{OA}_1 \leq_= \mathrm{OA}_2\), is defined as:
-\[ \exists R: \mpar{S_1 \times S_2} \to \formulae_{V_1 \uplus V_2}, \varphi_1 \uplus \varphi_2 \vdash R\mpar{i_1, i_2} \qwedge R \text{ hole-identical simulation of } \mathrm{OA}_1 \text{ in } \mathrm{OA}_2 \]
+If \(J_1 = J_2\) then ``\(A_1\) is a hole-identical refinement of \(A_2\)", noted \(A_1 \leq_= A_2\), is defined as:
+\[ \exists R: \mpar{S_1 \times S_2} \to \rformulae{V_1 \uplus V_2}, \varphi_1 \uplus \varphi_2 \vdash R\mpar{i_1, i_2} \qwedge R \text{ hole-identical simulation of } A_1 \text{ in } A_2 \]
 \end{defi}
-As in other simulation-like relations, \(R\) is a witness of \(\mathrm{OA}_1 \leq_= \mathrm{OA}_2\).
+As in other simulation-like relations, \(R\) is a witness of \(A_1 \leq_= A_2\).
 The standard requirements for (bi)simulations are that \(R\) relates initial states, transitions can be matched, and target of matched transitions with related sources are also related.
@@
 \begin{defi}[Hole-identical simulation]
-\Quentin{``\(R\) is a hole-identical simulation of \(\mathrm{OA}_1\) in \(\mathrm{OA}_2\)"}{Any idea on how to note that? \(R \vDash \mathrm{OA}_1 \leq_= \mathrm{OA}_2\) for instance.} is defined as:
+\Quentin{``\(R\) is a hole-identical simulation of \(A_1\) in \(A_2\)"}{Any idea on how to note that? \(R \vDash A_1 \leq_= A_2\) for instance.} is defined as:
 \begin{multline*}
@@
 	\end{array}} \\
-	\wedge \forall \sigma: \mpar{V_1 \uplus V_2} \to \values, \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \mathrm{OT}\mpar{s_2}} \mathit{guard}\mpar{t_2} \implies \bigvee_\subbox{t_1 \in \mathrm{OT}\mpar{s_1}} \mathit{guard}\mpar{t_1}
+	\wedge \forall \sigma: \mpar{V_1 \uplus V_2} \to \values, \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
 \end{multline*}
@@
 The 3\textsuperscript{rd} line is the condition to ensure that transitions are not matched to incompatible ones:
-For all variable assignement of the two automata and all hole actions (quantification of \(\sigma\)), assuming that the states were related and the transition in \(\mathrm{OA}_1\) is possible (\(R\mpar{s_1, s_2} \wedge g_1\) part) then there is always a transition, not necessarily only one, which can be performed (\(g_{2x}\)), produce the same action (\(\alpha_1 = \alpha_{2x}\)), accept the same action from the holes (\(\beta_{1j} = \beta_{2xj}\)) and satisfy the predicate for relating the target states after variable update (\(R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\)).
+For all variable assignement of the two automata and all hole actions (quantification of \(\sigma\)), assuming that the states were related and the transition in \(A_1\) is possible (\(R\mpar{s_1, s_2} \wedge g_1\) part) then there is always a transition, not necessarily only one, which can be performed (\(g_{2x}\)), produce the same action (\(\alpha_1 = \alpha_{2x}\)), accept the same action from the holes (\(\beta_{1j} = \beta_{2xj}\)) and satisfy the predicate for relating the target states after variable update (\(R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\)).
 
-The notion of refinement here is stating that \(\mathrm{OA}_1\) is a refinement of \(\mathrm{OA}_2\) if \(\mathrm{OA}_1\) can be simulated in \(\mathrm{OA}_2\).
+The notion of refinement here is stating that \(A_1\) is a refinement of \(A_2\) if \(A_1\) can be simulated in \(A_2\).
 The hole-identical part is referring to the fact that holes indicies are the same and identical holes indicies have to perform the same actions.
 On top of that the last line ensures no deadlock introduction.
-It can be interpreted ``assuming the predicate holds and there is any possible transition in \(\mathrm{OA}_2\) (= no deadlock), then there must be a possible transition in \(\mathrm{OA}_1\) (= no deadlock)".
+It can be interpreted ``assuming the predicate holds and there is any possible transition in \(A_2\) (= no deadlock), then there must be a possible transition in \(A_1\) (= no deadlock)".
 It does not have to ensure that this transition isn't garbage or that the target states are related because the first part of the simulation already does it.
@@
 
-\begin{lem}[Equivalent definition] % equivalence between first part of the definition and simulation refinement
+\begin{lem}[Equivalent definition]
 \begin{gather*}
+\forall \mpar{s_1, s_2} \in S_1 \times S_2, \\
 \mpar{\everymath{\displaystyle}\begin{array}{l}
@@
 	\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in T_1, \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\[6pt]
-	\sigma \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \bigsymb{\exists} \OTx{2}{}{2}{2} \in T_2, \\[12pt]
-	\quad \sigma \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
+	\quad \mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} \OTx{2}{}{2}{2} \in T_2, \\[12pt]
+	\qquad \sigma \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
 \end{array}}
@@
 The reason is that the formulation used is compatible with SMT solver, the place where it will most probably be used in practise.
-\begin{proof}
-\item[\(\Rightarrow\):] \(\) % TODO HERE
-\item[\(\Leftarrow\):] \(\) % TODO HERE
+\begin{proof} Let \(\mpar{s_1, s_2} \in S_1 \times S_2\),
+\item[\(\Rightarrow\):] We admit the up formula as \(H_{def}\), let \(t_1 \defobject \OTx{1}{}{1}{1} \in T_1\) and \(\sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values\) be such that \(H_{source} \defobject \sigma \vdash R\mpar{s_1, s_2} \wedge g_1\).
+	\(H_{def}\) applied to \(t_1\) gives \(\mpar{t_{2x} \defobject \OTx{2}{x}{2x}{1} \in T_2}^{x \in X}\) and the property \(H_{tmp}\) to which we give \(\sigma\) to get
+	\[ H_{smt} \defobject \sigma \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+		\alpha_1 = \alpha_{2x} \wedge \bigwedge_{j \in J'_1} \beta_{1j} = \beta_{2xj} \\[12pt]
+		\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+	\end{array}} \]
+	Unfolding the definition of \(\sigma \vdash f\) where \(f\) is not a closed formula in \(H_{smt}\) gives an exists that we use to get \nmm{\nu: \biguplus_{x \in X} \fvars{t_{2x}} \to \values} and
+	\[ H_{valid} \defobject \sigma \uplus \nu \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+		\alpha_1 = \alpha_{2x} \wedge \bigwedge_{j \in J'_1} \beta_{1j} = \beta_{2xj} \\[12pt]
+		\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+	\end{array}} \]
+	\(R\mpar{s_1, s_2} \wedge g_1\) in \(H_{valid}\) does not depends on \(\nu\) so we can use \(H_{source}\) to prove it and get \(H_{cover}\).
+	\(H_{cover}\) is a disjunction that we can eliminate, action that gives a value \(x\) and
+	\[ H_{target}\mpar{x} \defobject \sigma \uplus \nu \vdash \alpha_1 = \alpha_{2x} \wedge \bigwedge_{j \in J'_1} \beta_{1j} = \beta_{2xj} \wedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \]
+	Now that we have a specific \(x\) we can say that in the bottom formula \(t_{2x}\) is a witness in \(T_2\).
+	By doing that, what we are left to prove is \nmm{\sigma \vdash \alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_1} \beta_{1j} = \beta_{2xj} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}}.
+	As a valuation for variables in \(\fvars{t_{2x}}\) we have \(\nu\), so \(H_{target}\mpar{x}\) concludes the proof.
+\item[\(\Leftarrow\):] We admit the bottom formula as \(H_{ref}\), let \(t_1 \defobject \OTx{1}{}{1}{} \in T_1\) % TODO HERE; quantify on all valuations to get t_{2\sigma}
 \end{proof}
@@
 \begin{proof}
-\item \emph{Reflexivity:} Let \(\mathrm{OA}\) be an open automaton with variables in \(V\).
+\item \emph{Reflexivity:} Let \(A\) be an open automaton with variables in \(V\).
 	The automaton variables on the right hand side of the relation will be noted \(v'\) for the equivalent variable \(v \in V\) in the automaton on the left hand side.
-	The simulation \nmm{R = \mset{\mpar{s, s} \mapsto \bigwedge_{v \in V} v = v'}{s \in S_1}} is a witness of \(\mathrm{OA} \leq \mathrm{OA}\).
+	The simulation \nmm{R = \mset{\mpar{s, s} \mapsto \bigwedge_{v \in V} v = v'}{s \in S_1}} is a witness of \(A \leq A\).
 	Checking it is a simple exercise left to the reader in order to understand how the definition works.
-\item \emph{Transitivity:} Let \(\mathrm{OA}_1, \mathrm{OA}_2, \mathrm{OA}_3\) be open automata with respectively variables in \(V_1, V_2, V_3\) and states \(S_1, S_2, S_3\).
-	And let \(R_{12}\) be a witness of \(\mathrm{OA}_1 \leq_= \mathrm{OA}_2\) and \(R_{23}\) be a witness of \(\mathrm{OA}_2 \leq_= \mathrm{OA}_3\).
+\item \emph{Transitivity:} Let \(A_1, A_2, A_3\) be open automata with respectively variables in \(V_1, V_2, V_3\) and states \(S_1, S_2, S_3\).
+	And let \(R_{12}\) be a witness of \(A_1 \leq_= A_2\) and \(R_{23}\) be a witness of \(A_2 \leq_= A_3\).
 	\[ R_{13}\mpar{s_1, s_3} \defobject \exists V_2, \bigvee_{s_2 \in S_2} R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \]
-	Where \(\exists S, P\), with \(S \defobject \mbrc{v_1, v_2, \cdots, v_\card{S}}\) a finite set of variables, means \(\exists v_1, \exists v_2, \cdots, \exists v_\card{S}, P\).
 
-	Now let's prove that \(R_{13}\) is a witness of \(\mathrm{OA}_1 \leq_= \mathrm{OA}_3\):
+	Now let's prove that \(R_{13}\) is a witness of \(A_1 \leq_= A_3\):
 	\begin{itemize}
@@
 \begin{defi}[Hole-subset refinement]
-If \(J_1 \subseteq J_2\) then ``\(\mathrm{OA}_1\) is a hole-subset refinement of \(\mathrm{OA}_2\)", noted \(\mathrm{OA}_1 \leq_\subseteq \mathrm{OA}_2\) is defined as:
-\[ \exists R: \mpar{S_1 \times S_2} \to \formulae_{V_1 \uplus V_2}, \varphi_1 \uplus \varphi_2 \vdash R\mpar{i_1, i_2} \wedge R \text{ hole-subset simulation of } \mathrm{OA}_1 \text{ in } \mathrm{OA}_2 \]
+If \(J_1 \subseteq J_2\) then ``\(A_1\) is a hole-subset refinement of \(A_2\)", noted \(A_1 \leq_\subseteq A_2\) is defined as:
+\[ \exists R: \mpar{S_1 \times S_2} \to \rformulae{V_1 \uplus V_2}, \varphi_1 \uplus \varphi_2 \vdash R\mpar{i_1, i_2} \wedge R \text{ hole-subset simulation of } A_1 \text{ in } A_2 \]
 \end{defi}
@@
 \begin{defi}[Hole-subset simulation]
-``\(R\) is a hole-subset simulation of \(\mathrm{OA}_1\) in \(\mathrm{OA}_2\)" is defined as:
+``\(R\) is a hole-subset simulation of \(A_1\) in \(A_2\)" is defined as:
 \begin{multline*}
@@
 	\end{array}} \\
-	\wedge \forall \sigma: \mpar{V_1 \uplus V_2} \to \values, \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \mathrm{OT}\mpar{s_2}} \mathit{guard}\mpar{t_2} \implies \bigvee_\subbox{t_1 \in \mathrm{OT}\mpar{s_1}} \mathit{guard}\mpar{t_2}
+	\wedge \forall \sigma: \mpar{V_1 \uplus V_2} \to \values, \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_2}
 \end{multline*}
@@
 \begin{defi}[Hole-matching refinement]
-If \(\card{J_1} = \card{J_2}\) then ``\(\mathrm{OA}_1\) is a hole-matching refinement of \(\mathrm{OA}_2\)", noted \(\mathrm{OA}_1 \leq_\# \mathrm{OA}_2\) is defined as:
+If \(\card{J_1} = \card{J_2}\) then ``\(A_1\) is a hole-matching refinement of \(A_2\)", noted \(A_1 \leq_\# A_2\) is defined as:
 \begin{multline*}
@@
 	\varphi_1 \uplus \varphi_2 \vdash R\mpar{i_1, i_2} \qwedge f\mpar{J_1 \setminus J_2} = J_2 \setminus J_1 \\
-	\wedge R \text{ hole-f-matching simulation of } \mathrm{OA}_1 \text{ in } \mathrm{OA}_2
+	\wedge R \text{ hole-f-matching simulation of } A_1 \text{ in } A_2
 \end{multline*}
@@
 \begin{defi}[Hole-f-matching simulation]
-\(R\) is a hole-f-matching simulation of \(\mathrm{OA}_1\) in \(\mathrm{OA}_2\) is defined as:
+\(R\) is a hole-f-matching simulation of \(A_1\) in \(A_2\) is defined as:
 \begin{multline*}
@@
 \begin{defi}[Open automata refinement]
-For any two open automata \(\mathrm{OA}_1 \defobject \OA{S_1}{i_1}{J_1}{V_1}{\varphi_1}{T_1}\) and \(\mathrm{OA}_2 \defobject \OA{S_2}{i_2}{J_2}{V_2}{\varphi_2}{T_2}\), ``\(\mathrm{OA}_1\) is a refinement of \(\mathrm{OA}_2\)", noted \(\mathrm{OA}_1 \leq \mathrm{OA}_2\), is defined as:
+For any two open automata \(A_1 \defobject \OA{S_1}{i_1}{J_1}{V_1}{\varphi_1}{T_1}\) and \(A_2 \defobject \OA{S_2}{i_2}{J_2}{V_2}{\varphi_2}{T_2}\), ``\(A_1\) is a refinement of \(A_2\)", noted \(A_1 \leq A_2\), is defined as:
 \begin{multline*}
-	\exists R: \mpar{S_1 \times S_2} \to \formulae_{V_1 \uplus V_2}, \exists f: J_1 \setminus J_2 \to J_2 \setminus J_1, \\
-	\varphi_1 \uplus \varphi_2 \vdash R\mpar{i_1, i_2} \wedge R \text{ f simulation of } \mathrm{OA}_1 \text{ in } \mathrm{OA}_2
+	\exists R: \mpar{S_1 \times S_2} \to \rformulae{V_1 \uplus V_2}, \exists f: J_1 \setminus J_2 \to J_2 \setminus J_1, \\
+	\varphi_1 \uplus \varphi_2 \vdash R\mpar{i_1, i_2} \wedge R \text{ f simulation of } A_1 \text{ in } A_2
 \end{multline*}
@@
 \begin{defi}[f simulation]
-\(R\) is a f simulation of \(\mathrm{OA}_1\) in \(\mathrm{OA}_2\) is defined as:
+\(R\) is a f simulation of \(A_1\) in \(A_2\) is defined as:
 \begin{multline*}
@@
 	\end{array}} \\
-	\wedge \forall \sigma: \mpar{V_1 \uplus V_2} \to \values, R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \mathrm{OT}\mpar{s_2}} \mathit{guard}\mpar{t_2} \implies \bigvee_\subbox{t_1 \in \mathrm{OT}\mpar{s_1}} \mathit{guard}\mpar{t_1}
+	\wedge \forall \sigma: \mpar{V_1 \uplus V_2} \to \values, R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
 \end{multline*}
@@
 % Explain definition, really needed
-The objective of the first part of this definition is to be able to simulate \(\mathrm{OA}_1\) in \(\mathrm{OA}_2\) when holes of the same name receive the same closed automaton while other holes receive ``compatible" closed automata.
+The objective of the first part of this definition is to be able to simulate \(A_1\) in \(A_2\) when holes of the same name receive the same closed automaton while other holes receive ``compatible" closed automata.
 % safety is no longer trivial, prove the safety

### 2021-04-20 2021-Refinement/Traffic_Lights_Spec.tex
Refinement v0e

\begin{tikzpicture}

\node[state,initial] (v1) at (150:4) {R};
\node[state] (v2) at (30:4) {G};
\node[state] (v3) at (270:4) {Y};

\draw (v1) edge[dir=220] node[below] {\OTd{\act{tick}}{R \mapsto \act{tick}}{}} (v1);
\draw (v1) edge[dir=150] node[left] {\OTd{\act{onRed}}{}{}} (v1);
\draw (v1) edge[dir=80] node[above] {\OTd{\tau}{C \mapsto \theta\mpar{x}, R \mapsto \act{set}\mpar{x}}{}} (v1);
\draw (v1) edge node {\OTd{\act{TurnGreen}}{R \mapsto \act{over}\mpar{x}, C \mapsto \delta\mpar{x}}{}} (v2);
\draw (v2) edge[dir=100] node {\OTd{\act{tick}}{R \mapsto \act{tick}}{}} (v2);
\draw (v2) edge[dir=30] node {\OTd{\act{onGreen}}{}{}} (v2);
\draw (v2) edge[dir=320] node {\OTd{\tau}{C \mapsto \theta\mpar{x}, R \mapsto \act{set}\mpar{x}}{}} (v2);
\draw (v2) edge node {\OTd{\act{TurnYellow}}{R \mapsto \act{over}\mpar{x}, C \mapsto \delta\mpar{x}}{}} (v3);
\draw (v3) edge[dir=340] node {\OTd{\act{tick}}{R \mapsto \act{tick}}{}} (v3);
\draw (v3) edge[dir=270] node {\OTd{\act{onYellow}}{}{}} (v3);
\draw (v3) edge[dir=200] node {\OTd{\tau}{C \mapsto \theta\mpar{x}, R \mapsto \act{set}\mpar{x}}{}} (v3);
\draw (v3) edge node {\OTd{\act{TurnRed}}{R \mapsto \act{over}\mpar{x}, C \mapsto \delta\mpar{x}}{}} (v1);

\end{tikzpicture}

### 2021-04-20 2021-Refinement/report.tex
Refinement v0e

@@
 \usepackage{unicode-math}
-\usepackage{xcolor}
+\usepackage{tikz}
+\usetikzlibrary{external}
+%\usepackage{hyperref}
+% \usepackage{xcolor}
 \AtBeginDocument{\renewcommand\setminus{\smallsetminus}}
@@
 
+\input{common.tex}
 \input{preamble.tex}
+\input{tikzmacros.tex}
 
@@
 % Re-read what refinement are used for
+
+% Give the examples
 
@@
 
+For a relation \(\wrel{}{}{}\) which uses a property \(P\) to prove that two element are related \(\forall x \, x', x \wrel{}{}{} x' \iff \exists w: P\mpar{x, x'}\), the fact that there is a valid witness \(w: P\mpar{x, x'}\) is noted \(\wrel{x}{x'}{w}\).
+
 \section{Open Automaton}
@@
 \defitem \(\fvars{e}\) is the set of unbound variables in \(e \in E\).
-\defitem The terms restricted to variables in \(V\) are \(\rterms{V} \defnotation \mset{t \in \terms}{\fvars{t} = \emptyset}\); \(\rterms{V} \subset \terms\).
-\defitem The formulae restricted to variables in \(V\) are \(\rformulae{V} \defnotation \mset{f \in \formulae}{\fvars{f} = \emptyset}\); \(\rformulae{V} \subset \terms\).
-\defitem The closed terms are terms restricted to variables in \(\emptyset\), \(\cterms\).
-\defitem The closed formulae are formulae restricted to variables in \(\emptyset\), \(\cformulae\).
+\defitem The expressions restricted to variables in \(V\) are \(E_V \defnotation \mset{e \in E}{\fvars{e} = \emptyset}\); \(E_V \subset E\).
+\defitem The closed expressions are expressions restricted to variables in \(\emptyset\), \(E_\emptyset\).
 \end{defi}
-By extension, expressions restricted to variables and closed expressions are also defined.
+By restriction, terms and formulae restricted to variables and closed versions are also defined.
 A closed expression is an expression without unbound variable.
+We can use the previous example of first order formula on Peano integers to illustrate these definitions.
+\(x\), \(S\mpar{y}\) are valid terms, \(0\) is a closed term, \(\fvars{x} = \mbrc{x}, \fvars{S\mpar{y}} = \mbrc{y}, \fvars{0} = \emptyset\).
+\(x = 0\), \(\forall y, \exists x, \mathit{sum}\mpar{y, z, x}\) are valid formulae, \(\forall x, \neg S\mpar{x} = 0\) is a valid closed formula, \(\fvars{x = 0} = \mbrc{x}, \fvars{\forall y, \exists x, \mathit{sum}\mpar{y, z, x}} = \mbrc{z}, \fvars{\forall x, \neg S\mpar{x} = 0} = \emptyset\).
 \begin{defi}[Interpretation, Values, Satisfiability, (Parallel) substitution]
 We assume that the following are given:
-\defitem The values \(\values\), which are interpretations of closed terms;
-\defitem The validity relation on closed formulae, \({\vdash} \subseteq \cformulae\);
-\defitem The substitution in \(e \in E\) of \(x \in \fvars{e}\) by \(t \in \terms\), \(e\subst{t}{x}\);
+\defitem The values \(\values\), which are interpretations of closed terms.
+\defitem The validity relation on closed formulae, \({\vdash} \subseteq \cformulae\).
+\defitem The substitution in \(e \in E\) of \(x \in \fvars{e}\) by \(t \in \terms\), \(e\subst{t}{x}\).
 \defitem The parallel substitution in \(e \in E\) of variables in \(V\) by \(\psi: V \to \terms\), \(e\psubst{\psi}\).
@@
 In the case where it is not, the variables in \(V \setminus \fvars{e}\) are not substituted.
-The substitutions might give a nonsensical expression; for instance let the terms be integers and pairs with (pointwise) addition, \(\mpar{a + b}\psubst{a \mapsto 7, b \mapsto \mpar{4, 5}}\) is not a valid term.
+The substitutions might give a nonsensical expression; for instance let the terms be integers and pairs with (pointwise) addition, \(\mpar{a + b}\psubst{a \mapsto 7, b \mapsto \mpar{4, 5}}\) is a ill-formed term.
 This can be guarded with the atom \(e\subst{t}{x} \in E\) and \(e\psubst{\psi} \in E\) and it will implicitely be the case, for instance when there is quantification on \(t\) and \(\psi\), to simplify notations.
@@
 While this is correct when \(\values \subseteq \cterms\), in the other cases this will be used as a shorthand for substitution with any term which can be interpreted as \(v\).
+We suppose that the interpretation of terms is compatible w.r.t.\@ substitution, that is if two terms \(t\), \(t'\) are interpreted with the same value, then replacing \(t\) by \(t'\) in a well-formed expression makes an equivalent well-formed expression.
 A quantifier followed by a finite set will be used as a shorthand for the quantification on every variable in the set, for instance \(\forall A, \exists B, P\) with \(A = \mbrc{a_1, \dots, a_\card{A}}, B = \mbrc{b_1, \dots, b_\card{B}}\) means \(\forall a_1, \dots, \forall a_\card{A}, \exists b_1, \dots, \exists b_\card{B}, P\).
@@
 
+To illustrate these definitions let's look at two implementations (figure \ref{fig:enable}) of the LOTOS\marginpar{cite something here} operator enable in the open automata model.
+The enable operator runs its the left hand side agent until it chooses to finish, at which point it produces an action \(\delta\) that is synchronised with the first action of the right hand side agent which must be \(\act{acc}\), then only the latter agent runs.
+During the synchronised action \Quentin{data can be exchanged}{I need to read a little bit more on that; is that a return code?}. % TODO: read
+\begin{figure}
+\centering
+\input{enable_state.tex}
+\vrule
+\input{enable_var.tex}
+\caption{Enable operator, on the left state oriented, on the right variable oriented.}
+\label{fig:enable}
+\end{figure}
+\begin{exi}[Enable, state-oriented]
+To draw automata, the usual circle for states and simple arrows for transitions convention is used.
+The initial state is indicated by a double circle.
+States names are indicated inside the circles and transitions labels are drawn near their corresponding arrow.
+
+The open transitions do not indicate the source and target states since that is the role of the transitions arrows; only the action is on the bottom side of the open transition.
+Also in the example, transitions are specified using variables in place of actions or values.
+This is used to represent all the transitions created by a correct substitution of these variables, as there are often infinitly many.
+
+There is a model where open automata have finitely many transitions and variables like that are allowed in the expressions and in the action data, not as a tool to graphically represent an infinity of transitions but as a real construct.
+This model is the model of structural open automata as opposed to the model used here of semantic open automata.
+The structural version is more adapted to uses where the object manipulated must be finite, for example in algorithms, whereas the semantic version avoids the manipulation of substitutions, which simplifies proofs.
+
+Let's get back to the example.
+The open automata drawn on the left is \(\OA{\mbrc{L, R}}{L}{\emptyset}{\mbrc{}}{\mbrc{l, r}}{T}\) where transitions in \(T\) are all the valid transitions for any substitution of \(x\) and \(y\) of
+\begin{align*}
+	\OT{L}{L}{x}{\mbrc{l \mapsto x}}{x \neq \delta}{\mbrc{}} &&
+	\OT{L}{R}{\tau}{\mbrc{l \mapsto \delta\mpar{x}, r \mapsto \act{acc}\mpar{y}}}{x = y}{\mbrc{}} &&
+	\OT{R}{R}{x}{\mbrc{r \mapsto x}}{\top}{\mbrc{}}
+\end{align*}
+% TODO: Explain example
+\end{exi}
+\begin{exi}[Enable, variable-oriented]
+% TODO: Explain example
+\end{exi}
+
 Now we can define some utilitary functions:
@@
 	\fguard{\OTg} & \defnotation g &
-	\mathit{target}\mpar{\OTg} & \defnotation s' \\
-	\mathit{Post}\mpar{\OTg} & \defnotation \psi &
 	\fOT{s} & \defnotation \mbrc{\OTg \in T}
@@
 \begin{defi}[Simulation on open automata]
-A relation \(\leq\) is a simulation iff for any two related automata \(\OA{S_1}{i_1}{J_1}{V_1}{\varphi_1}{T_1} \leq \OA{S_2}{i_2}{J_2}{V_2}{\varphi_2}{T_2}\), there is a relation under predicate between their states \(R: S_1 \times S_2 \to \rformulae{V_1 \uplus V_2}\) that satisfies both
+A relation \(\leq\) is a simulation if for any related automata \(\wrel{A_1}{A_2}{R}\) where \(A_1 \defobject \OA{S_1}{i_1}{J_1}{V_1}{\varphi_1}{T_1}\), \(A_2 \defobject \OA{S_2}{i_2}{J_2}{V_2}{\varphi_2}{T_2}\) and \(R: S_1 \times S_2 \to \rformulae{V_1 \uplus V_2}\), \(R\) satisfies both
 \defitem Initial states are related under initial valuations: \(\varphi_1 \uplus \varphi_2 \vdash R\mpar{i_1, i_2}\);
@@
 
-\begin{defi}[Deadlock reduction]
-A simulation \(\leq\) is deadlock reducing if for all related automata \(A_1 \leq A_2\), where \(A_1 \defobject \OA{S_1}{i_1}{V_1}{\varphi_1}{J_1}{T_1}\) and \(A_2 \defobject \OA{S_2}{i_2}{V_2}{\varphi_2}{J_2}{T_2}\), there is a witness \(R: S_1 \times S_2 \to \rformulae{V_1 \uplus V_2}\) of the fact that it is a simulation that also satisfies
+\begin{defi}[Deadlock reduction, intuitive definition]
+A simulation \(\leq\) is deadlock reducing if in all the \(R: S_1 \times S_2 \to \rformulae{V_1 \uplus V_2}\) such that \(\wrel{A_1}{A_2}{R}\), there is one that also satisfies
 \begin{multline*}
@@
 In particular filling a hole with the deadlock automaton (only one state without out-transitions) is not considered a refinement for a no deadlock reducing simulation refinement.
-A way to solve this issue is to caracterise a correct composition that will be used instead of the composition introduced earlier.
-\begin{defi}[Correct composition]
-The composition \(A_p\subst{A_c}{k} \defobject \OA{S}{i}{V}{\varphi}{J}{T}\) where \(A_c \defobject \OA{S_c}{i_c}{V_c}{\varphi_c}{J_c}{T_c}\), \(k \in J_p\) and \(A_p \defobject \OA{S_p}{i_p}{V_p}{\varphi_p}{J_p}{T_p}\), is a correct composition if there is a predicate on its states \(p: S \to \rformulae{V}\) that satisfies both
-\defitem Being valid on initial states under initial valuation: \(\varphi \vdash p\mpar{i}\)
+A way to solve this issue is to caracterise a composition that do not introduce deadlocks, which will be used instead of the composition introduced earlier.
+\begin{defi}[Reachability]
+For any open automata \(A \defobject \OA{S}{i}{V}{\varphi}{J}{T}\), we define the caracterisation of reachable valuations \(\reach{A}: S \to \rformulae{V}\) as the strongest predicate on states such that
+\defitem \(\varphi \vdash \reach{A}\mpar{i}\);
+\defitem \(\forall \OTg \in T, \vdash \reach{A}\mpar{s} \implies \reach{A}\mpar{s'}\psubst{\psi}\).
+\end{defi}
+The caracterisation of reachable valuations is used to caracterise the states and valuations that are reachable in a run of an automaton.
+For a valuation \(\sigma: V \to \values\) and a state \ % TODO HERE
+\begin{defi}[Non-locking composition] % TODO: définir un prédicat d'accessibilité plutôt qu'utiliser un p, faire deux définitions puis un lemme d'équivalence plutôt que def+lem
+The composition \(A_p\subst{A_c}{k} \defobject \OA{S}{i}{V}{\varphi}{J}{T}\) where \(A_c \defobject \OA{S_c}{i_c}{V_c}{\varphi_c}{J_c}{T_c}\), \(k \in J_p\) and \(A_p \defobject \OA{S_p}{i_p}{V_p}{\varphi_p}{J_p}{T_p}\), is a correct composition if there is a predicate on its states \(p: S \to \rformulae{V}\) that satisfies
+\defitem Being valid on initial states under initial valuation: \(\varphi \vdash p\mpar{i}\);
+\defitem Transfering validity across transitions: \(\forall \OTg \in T, \vdash p\mpar{s} \implies p\mpar{s'}\psubst{\psi}\);
 \defitem From states where the predicate is valid, if a transition was possible in \(A_p\) then a transition is possible in \(A\) and the predicate holds in the target state:
-\[ \forall s \in S, \sigma: V \to \values, \mpar{\exists t_p \in \fOT{\pi_{S_p}\mpar{s}}, \sigma \vdash p\mpar{s} \wedge \fguard{t_p}} \implies \bigsymb{\exists} \OTg \in T, \sigma \vdash g \wedge p\mpar{s'}\psubst{\psi} \]
+\[ \forall s \in S, \sigma: V \to \values, \mpar{\exists t_p \in \fOT{\pi_{S_p}\mpar{s}}, \sigma \vdash p\mpar{s} \wedge \fguard{t_p}} \implies \bigsymb{\exists} \OTg \in T, \sigma \vdash g \]
 \end{defi}
@@
 	\[ \mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} \OTx{2}{}{2}{2} \in T_2, \sigma \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \]
-	The left part of the implication is the left side of \hyp{g2} so we get \(t'_2 \in T_2\) and what's after as the hypothesis \hyp{t}.
-	The witnesses for \goal{G1} are \(t'_2\) and \(t_1\), and the rest is proved with a combination of \hyp{t} and \hyp{g1}.
+	The left part of the implication is the left side of \hyp{g2} so we get \(t'_2 \in T_2\) and what's after as the hypothesis \hyp{target}.
+	The witnesses for \goal{G1} are \(t'_2\) and \(t_1\), and the rest is proved with a combination of \hyp{target} and \hyp{g1}.
 \end{proof}
@@
 The second part of the formula in the definition of correct composition is equivalent to the following:
-\[ \forall s \in S, \vdash p\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \mpar{\fguard{t} \wedge p\mpar{\mathit{target}\mpar{t}}\psubst{\mathit{Post}\mpar{t}}} \]
+\[ \forall s \in S, \vdash p\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
 \end{lem}
-\begin{proof}
-% TODO HERE
+\begin{proof} % TODO HERE
+\item[\(\implies\):] % TODO
+\item[\(\impliedby\):] % TODO
 \end{proof}
@@
 % TODO: Some equivalences
-``Composition completeness" can be modified into ``Deadlock reduction completeness" to be compatible with ``Deadlock reduction": \(\forall a\, b, a\mbrk{b} \sqsubseteq a \implies a\mbrk{b} \leq a\).
-Only the latter will be considered.
-Similar issues arise on other properties and can be fixed by changing the prerequisites to insure that the most deadlock-prone composition of automata is composition complete:
-\begin{description}
-\item[Composition context equivalence modified:] \(\forall a\, b\, c, a \leq b \wedge a\mbrk{c} \leq a \implies a\mbrk{c} \leq b\mbrk{c}\);
-\item[Composition congruence modified:] \(\forall a\, b\, c, a \leq b \wedge c\mbrk{a} \leq c \implies c\mbrk{a} \leq c\mbrk{b}\);
-\item[Composition compatibility modified:] \(\forall a\, b\, c\, d, a \leq b \wedge c \leq d \wedge c\mbrk{a} \leq c \implies c\mbrk{a} \leq d\mbrk{b}\);
-\end{description}
+% ``Composition completeness" can be modified into ``Deadlock reduction completeness" to be compatible with ``Deadlock reduction": \(\forall a\, b, a\mbrk{b} \sqsubseteq a \implies a\mbrk{b} \leq a\).
+% Only the latter will be considered.
+% Similar issues arise on other properties and can be fixed by changing the prerequisites to insure that the most deadlock-prone composition of automata is composition complete:
+% \begin{description}
+% \item[Composition context equivalence modified:] \(\forall a\, b\, c, a \leq b \wedge a\mbrk{c} \leq a \implies a\mbrk{c} \leq b\mbrk{c}\);
+% \item[Composition congruence modified:] \(\forall a\, b\, c, a \leq b \wedge c\mbrk{a} \leq c \implies c\mbrk{a} \leq c\mbrk{b}\);
+% \item[Composition compatibility modified:] \(\forall a\, b\, c\, d, a \leq b \wedge c \leq d \wedge c\mbrk{a} \leq c \implies c\mbrk{a} \leq d\mbrk{b}\);
+% \end{description}
 
@@
 \begin{defi}[Hole-identical simulation]
-\Quentin{``\(R\) is a hole-identical simulation of \(A_1\) in \(A_2\)"}{Any idea on how to note that? \(R \vDash A_1 \leq_= A_2\) for instance.} is defined as:
+\Quentin{``\(R\) is a hole-identical simulation of \(A_1\) in \(A_2\)"}{Any idea on how to note that?
+\(R \vDash A_1 \leq_= A_2\) for instance.} is defined as: % TODO: faire des macros, + A_1 \overset{=}\leq_R A_2
 \begin{multline*}

### 2021-04-21 2021-Refinement/report.tex
Introducing some examples, removing pdf, correcting some line ends

@@
 \usetikzlibrary{external}
-%\usepackage{hyperref}
+% \usepackage{hyperref}
 % \usepackage{xcolor}
@@
 % transitions between sections
-% Re-read what refinement are used for
-
-% Give the examples
+% Re-read what refinement are used for, LOTOS
+% read CCSL and BIP
 
@@
 To define an open automaton we need some preliminary definitions.
-\begin{defi}[Expression algebra, Formulae, Terms]
-An expression algebra \(E\) is a disjoint union \(E \defobject \terms \uplus \formulae\) where \(\terms\) is a term algebra and \(\formulae\) the formulae over \(\terms\).
+\begin{defi}[Expression algebra, Action algebra, Formulae, Terms]
+An expression algebra \(E\) is a disjoint union \(E \defobject \terms \uplus \actions \uplus \formulae\) of the terms, the actions and the formulae.
+
+The terms \(\terms\) is a term algebra.
+The action algebra \(\actions\) is the set of pairs \(\labels \times \terms\) where \(\labels\) are the action labels.
+The formulae \(\formulae\) are at least the first order formulae over \(\terms\) and \(\labels\).
 \end{defi}
-The terms algebra is arbitrary.
-The formulae form a first order logic over \(\terms\) and some relations.
+The term algebra and action labels are arbitrary.
+An element \(\mpar{l, t} \in \actions\) is noted \(l\mpar{t}\).
+The formulae form at least a first order logic with an equality relation that is not necessarily the equality on \(\terms\).
+
 An example of term algebra can be Peano integers (zero, variable and successor function), the formulae associated can use equality relation, \(\mathit{sum}\mpar{a, b, c} \defobject a = b + c\) relation and \(\mathit{prod}\mpar{a, b, c} \defobject a = b \times c\) relation.
@@
 \defitem \(\fvars{e}\) is the set of unbound variables in \(e \in E\).
-\defitem The expressions restricted to variables in \(V\) are \(E_V \defnotation \mset{e \in E}{\fvars{e} = \emptyset}\); \(E_V \subset E\).
+\defitem The expressions restricted to variables in \(V\) are \(E_V \defnotation \mset{e \in E}{\fvars{e} \subseteq V}\); \(E_V \subset E\).
 \defitem The closed expressions are expressions restricted to variables in \(\emptyset\), \(E_\emptyset\).
 \end{defi}
-By restriction, terms and formulae restricted to variables and closed versions are also defined.
-A closed expression is an expression without unbound variable.
+Terms, actions and formulae restricted to variables and their closed versions are also defined by restriction.
+A closed expression can contain variables, only unbound variable are restricted.
+
 We can use the previous example of first order formula on Peano integers to illustrate these definitions.
-\(x\), \(S\mpar{y}\) are valid terms, \(0\) is a closed term, \(\fvars{x} = \mbrc{x}, \fvars{S\mpar{y}} = \mbrc{y}, \fvars{0} = \emptyset\).
-\(x = 0\), \(\forall y, \exists x, \mathit{sum}\mpar{y, z, x}\) are valid formulae, \(\forall x, \neg S\mpar{x} = 0\) is a valid closed formula, \(\fvars{x = 0} = \mbrc{x}, \fvars{\forall y, \exists x, \mathit{sum}\mpar{y, z, x}} = \mbrc{z}, \fvars{\forall x, \neg S\mpar{x} = 0} = \emptyset\).
+\(x\), \(S\mpar{y}\) are valid terms, \(0\) is a closed term, \(\fvars{x} = \mbrc{x}\), \(\fvars{S\mpar{y}} = \mbrc{y}\), \(\fvars{0} = \emptyset\).
+\(x = 0\), \(\forall y, \exists x, \mathit{sum}\mpar{y, z, x}\) are valid formulae, \(\forall x, \neg S\mpar{x} = 0\) is a valid closed formula, \(\fvars{x = 0} = \mbrc{x}\), \(\fvars{\forall y, \exists x, \mathit{sum}\mpar{y, z, x}} = \mbrc{z}\), \(\fvars{\forall x, \neg S\mpar{x} = 0} = \emptyset\).
+
 \begin{defi}[Interpretation, Values, Satisfiability, (Parallel) substitution]
@@
 \defitem The values \(\values\), which are interpretations of closed terms.
-\defitem The validity relation on closed formulae, \({\vdash} \subseteq \cformulae\).
+\defitem The validity relation on closed formulae, \({\vdash} \subseteq \rformulae\).
 \defitem The substitution in \(e \in E\) of \(x \in \fvars{e}\) by \(t \in \terms\), \(e\subst{t}{x}\).
@@
 In the case where it is not, the variables in \(V \setminus \fvars{e}\) are not substituted.
-The substitutions might give a nonsensical expression; for instance let the terms be integers and pairs with (pointwise) addition, \(\mpar{a + b}\psubst{a \mapsto 7, b \mapsto \mpar{4, 5}}\) is a ill-formed term.
+The substitutions might give a ill-formed expression; for instance let the terms be integers and pairs with (pointwise) addition, \(\mpar{a + b}\psubst{a \mapsto 7, b \mapsto \mpar{4, 5}}\) is a ill-formed term.
 This can be guarded with the atom \(e\subst{t}{x} \in E\) and \(e\psubst{\psi} \in E\) and it will implicitely be the case, for instance when there is quantification on \(t\) and \(\psi\), to simplify notations.
@@
 The interpretation of terms is supposed to be decidable.
-The validity of formulae might not be decidable nor complete nor consistent, however we will pretend like they are because these are really hard problems for logicians that we don't want to deal with.\footnote{In practise a term algera with only equality is used, and it is has all these properties.}
+The validity of formulae might not be decidable nor complete nor consistent, however we will pretend like they are because these are really hard problems for logicians that we don't want to deal with.
+In practise the formulae will be given to a SMT solver and we make sure they have all the previous properties.
 
 A value \(v\) may be used for keeping a variable state, and then injected in terms for substitution.
-While this is correct when \(\values \subseteq \cterms\), in the other cases this will be used as a shorthand for substitution with any term which can be interpreted as \(v\).
+While this is correct when \(\values \subseteq \rterms\), in the other cases this will be used as a shorthand for substitution with any term which can be interpreted as \(v\).
 We suppose that the interpretation of terms is compatible w.r.t.\@ substitution, that is if two terms \(t\), \(t'\) are interpreted with the same value, then replacing \(t\) by \(t'\) in a well-formed expression makes an equivalent well-formed expression.
-A quantifier followed by a finite set will be used as a shorthand for the quantification on every variable in the set, for instance \(\forall A, \exists B, P\) with \(A = \mbrc{a_1, \dots, a_\card{A}}, B = \mbrc{b_1, \dots, b_\card{B}}\) means \(\forall a_1, \dots, \forall a_\card{A}, \exists b_1, \dots, \exists b_\card{B}, P\).
+In a formula, a quantifier followed by a finite set will be used as a shorthand for the quantification on every variable in the set, for instance \(\forall A, \exists B, P\) with \(A = \mbrc{a_1, \dots, a_\card{A}}, B = \mbrc{b_1, \dots, b_\card{B}}\) means \(\forall a_1, \dots, \forall a_\card{A}, \exists b_1, \dots, \exists b_\card{B}, P\).
+% maybe Valuation as formula /\ var=val
 
-The validity relations will be noted using the classical relational notation \(\vdash f \defnotation {f \in {\vdash}}\).
+The validity relations will be noted using the classical relational notation \(\vdash f\).
+The precedence of \(\vdash\) is the lowest on the right side and higher than \(\uplus\) on the left side: \(\forall a \, b, a \uplus b \vdash x \wedge y \implies \exists z, P\mpar{x,z}\) is the same as \(\forall a \, b, \mpar{\mpar{a \uplus b} \vdash \mpar{\mpar{x \wedge y} \implies \exists z, P\mpar{x,z}}}\).
 The usual validity of a formula \(f \in \formulae\) is noted \({\vdash f} \defnotation {\vdash \forall \fvars{f}, f}\).
-The usual validity of a formula \(f \in \formulae\) with some fixed valuation \(\sigma: V \to \values\) is noted \({\sigma \vdash f} \defnotation {\vdash \forall\mpar{\fvars{f} \setminus V}, f\psubst{\sigma}}\).
+The usual validity of a formula \(f \in \formulae\) with some fixed valuation \(\sigma: V \to \values\) is noted \({\sigma \vdash f} \defnotation {\vdash \forall \fvars{f\psubst{\sigma}}, f\psubst{\sigma}}\).
+% TODO: remettre en exists?
+faire des LHS plus compliques style forall LHS exists RHS
+% maybe satisfiability with formulas on the LHS (and variabl sets)
 
@@
 \begin{defi}[Open automaton]
-A semantic open automaton is a tuple \(\OA{S}{i}{V}{\varphi}{J}{T}\) with \(S\) the set of states, \(i \in S\) the initial state, \(V\) the set of variable names unique to this automaton, \(\varphi: V \to \values\) the initial valuation of variables, \(J\) the set of hole names and \(T\) a set of open-transitions.
+A semantic open automaton is a tuple \(\OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(S\) the set of states, \(s_0 \in S\) the initial state, \(V\) the set of variable names unique to this automaton, \(\sigma_0: V \to \values\) the initial valuation of variables, \(J\) the set of hole names and \(T\) a set of open-transitions.
 
-\(S, V, J\) are arbitrary sets, only \(J\) is required to be finite.
+\(S, V, J\) are arbitrary finite sets.
 \end{defi}
@@
 \begin{defi}[Open transition]
-A semantic open transition is a tuple \nmm{\OT{s}{s'}{\alpha\mpar{v_\alpha}}{\mpar{\beta_j\mpar{v_{\beta j}}}^{j \in J'}}{g}{\psi}} with \(s, s' \in S\) the source and target states, \(\alpha \in \actions\) an action label, \(J' \subseteq J\) the holes involved, \(\beta_j \in \actions\) the action labels of the holes, \(v_\alpha \in \rterms{V}\) the emitted action, \(v_{\beta j}^{j \in J'} \in \rterms{V}\) the hole actions, \(g \in \rformulae{V}\) the guard and \(\psi: V \to \rterms{V}\) the new value of the variables.
+A semantic open transition is a tuple \nmm{\OTg} with \(s, s' \in S\) the source and target states, \(\alpha \in \ractions\) the produced action, \(J' \subseteq J\) the holes involved, \(\beta_j \in \ractions\) the actions of the holes, \(g \in \rformulae[V]\) the guard and \(\psi: V \to \rterms\) the new value of the variables.
 \end{defi}
-The set of action labels \(\actions\) is arbitrary and implicit.
-To simplify formulae, the notations \(\alpha \defnotation \alpha\mpar{v_\alpha}\) and \(\alpha = \beta \defnotation \alpha = \beta \wedge v_\alpha = v_\beta\) will be used.
+The intuition of a semantic open automaton is a partially defined LTS with variables, guards on transitions and parametrised actions.
+Initially the automaton is in the initial state with the initial valuation.
+In any state with any valuation, it can perform transitions which source state is the current state and which guard is valid in the current valuation if the holes emit the indicated action.
+By performing the transition the automaton emits the indicated action and updates its variables and state.
 
-To illustrate these definitions let's look at two implementations (figure \ref{fig:enable}) of the LOTOS\marginpar{cite something here} operator enable in the open automata model.
-The enable operator runs its the left hand side agent until it chooses to finish, at which point it produces an action \(\delta\) that is synchronised with the first action of the right hand side agent which must be \(\act{acc}\), then only the latter agent runs.
-During the synchronised action \Quentin{data can be exchanged}{I need to read a little bit more on that; is that a return code?}. % TODO: read
 \begin{figure}
@@
 \input{enable_var.tex}
-\caption{Enable operator, on the left state oriented, on the right variable oriented.}
+\caption{Enable operator implementation with open automata, on the left state oriented, on the right variable oriented}
 \label{fig:enable}
 \end{figure}
+To illustrate these definitions let's look at two implementations (figure \ref{fig:enable}) of the LOTOS\marginpar{cite something here} operator enable in the open automata model.
+The enable operator runs its the left hand side agent until it chooses to finish, at which point it produces an action \(\delta\) that is synchronised with the first action of the right hand side agent which must be \(\act{acc}\), then only the latter agent runs.
+During the synchronised action \Quentin{data can be exchanged}{I need to read a little bit more on that; is that a return code?}.
 \begin{exi}[Enable, state-oriented]
@@
 Also in the example, transitions are specified using variables in place of actions or values.
-This is used to represent all the transitions created by a correct substitution of these variables, as there are often infinitly many.
+This is used to represent all the transitions created by a correct substitution of these variables, which cannot be drawn otherwise as there are often infinitly many.
 
-There is a model where open automata have finitely many transitions and variables like that are allowed in the expressions and in the action data, not as a tool to graphically represent an infinity of transitions but as a real construct.
-This model is the model of structural open automata as opposed to the model used here of semantic open automata.
+There is a model where open automata have finitely many transitions and variables like that are allowed in any expression, not only as a tool to graphically represent an infinity of transitions but as a real construct.
+This model is the structural open automata as opposed to the model used here of semantic open automata.
 The structural version is more adapted to uses where the object manipulated must be finite, for example in algorithms, whereas the semantic version avoids the manipulation of substitutions, which simplifies proofs.
@@
 Let's get back to the example.
-The open automata drawn on the left is \(\OA{\mbrc{L, R}}{L}{\emptyset}{\mbrc{}}{\mbrc{l, r}}{T}\) where transitions in \(T\) are all the valid transitions for any substitution of \(x\) and \(y\) of
+The automata on the left side is \(\OA{\mbrc{L, R}}{L}{\emptyset}{\mbrc{}}{\mbrc{l, r}}{T}\) where transitions in \(T\) are generated by all valid substitution of \(x\) and \(y\) in
 \begin{align*}
@@
 \end{align*}
-% TODO: Explain example
+Note that we could have expressed the transition in the middle with \(\mbrc{l \mapsto \delta\mpar{x}, r \mapsto \act{acc}\mpar{x}}\) wich would have avoided many transitions with trivially false guards like the one where \(x \mapsto 1, y \mapsto 2\) which has the guard \(1 = 2\).
+
+This automaton is an implementation of the enable operator because it begins in the state \(L\) where it allows any transition from its hole \(l\) which is not \(\delta\) then synchronises its holes on the same data, effectively allowing a data exchange when it goes into state \(R\), and finally allows any transition from its hole \(r\).
+Only the synchronisation is hidden to the exterior by sending a \(\tau\) which is usually a silent action always allowed, unsynchronised with other holes and passed unmodified.
+Well here \(\tau\) is not always allowed from the holes in the state \(L\) the hole \(r\) cannot emmit it for the sake of simplifying the first example of open automaton.
 \end{exi}
 \begin{exi}[Enable, variable-oriented]
-% TODO: Explain example
+The automata drawn on the right side of the figure is an alternative implementation of the enable operator which has already been proven equivalent in previous work by ...\marginpar{cite sth here}.
+The drawing introduces the double arrows which is used to denote the initial valuation.
+The automata drawn is \(\OA{\mbrc{\_}}{\_}{\mbrc{v}}{l^\mbrc{v}}{\mbrc{l, r}}{T}\) where transitions in \(T\) are like previously all the transitions generated by valid substitution of \(x\) and \(y\) in
+\begin{align*}
+	\OT{\_}{\_}{x}{\mbrc{l \mapsto x}}{v = l \wedge x \neq \delta}{\mbrc{}} &&
+	\OT{\_}{\_}{\tau}{\mbrc{l \mapsto \delta\mpar{x}, r \mapsto \act{acc}\mpar{y}}}{v = l \wedge x = y}{\mbrc{v \gets r}} &&
+	\OT{\_}{\_}{x}{\mbrc{r \mapsto x}}{v = r}{\mbrc{}}
+\end{align*}
+Note that in this example \(r\) is a hole name and also a closed term, but not a variable.
+The same applies for \(l\).
+\(v\) is a variable name for the automaton and a variable in the guard, but its value is not substituted.
+If an automaton variable \(v\) is in a transition outside of the guard then it would mean that, any transition obtained by valid substitution of \(v\) with a value \(x\) and by adding \(v = x\) to the guard, would be a transition of the automaton.
+
+% TODO: run the automaton conceptually
 \end{exi}
 
-Now we can define some utilitary functions:
+Finally we can define some utilitary functions:
 \begin{defi}[Guard, Out-transition]
@@
 \end{defi}
-The intuition of a semantic open automaton is a partially defined LTS with variables, guards on transitions and parametrised actions.
 From this point semantic open automata and open transitions will be called automata and transitions for simplicity.
@@
 % TODO: Intro
-When the auomaton is in a state \(s \in S\) with a valuation of its variables \(\sigma: V \to \values\), it cannot perform transitions \nmm{\OTg \in T} such that \(\neg g\psubst{\sigma}\).
-After performing the transition and emitting action \(\alpha\), the automaton is in the state \(s'\) with valuation \(\psi\psubst{\sigma}\).
-The holes are synchronised using a handshake like mecanism when the transition happens.
-\begin{exi}
-\end{exi}
 
@@
 \begin{defi}[Composition of open automata]
-The composition of \(A_c \defobject \OA{S_c}{i_c}{V_c}{\varphi_c}{J_c}{T_c}\) in the hole \(k \in J_p\) of \(A_p \defobject \OA{S_p}{i_p}{V_p}{\varphi_p}{J_p}{T_p}\) is
+The composition of \(A_c \defobject \OA{S_c}{s_{0c}}{V_c}{\sigma_{0c}}{J_c}{T_c}\) in the hole \(k \in J_p\) of \(A_p \defobject \OA{S_p}{s_{0p}}{V_p}{\sigma_{0p}}{J_p}{T_p}\) is
 \begin{align*}
-	A_p\subst{A_c}{k} \defnotation & \OA{S_p \times S_c}{\mpar{i_p, i_c}}{V_p \uplus V_c}{\varphi_p \uplus \varphi_c}{J_c \uplus J_p \setminus \mbrc{k}}{T} \\
+	A_p\subst{A_c}{k} \defnotation & \OA{S_p \times S_c}{\mpar{s_{0p}, s_{0c}}}{V_p \uplus V_c}{\sigma_{0p} \uplus \sigma_{0c}}{J_c \uplus J_p \setminus \mbrc{k}}{T} \\
 	\text{With } T \defobject & \mset{\OT{\mpar{s_p, s_c}}{\mpar{s'_p, s'_c}}{\alpha_p}{\beta_j^{j \in J'_c \uplus J'_p \setminus \mbrc{k}}}{g_p \wedge g_c \wedge \alpha_c = \beta_k}{\psi_p \uplus \psi_c}}{\OTx{p}{}{}{p} \in T_p, \OTx{c}{}{}{c} \in T_c} \\
@@
 \begin{exi}
+\begin{figure}
+\centering
+\input{Traffic_Lights_Spec.tex}
+\caption{The specification of a traffic light system}
+\label{fig:tls}
+\end{figure}
+\begin{figure}
+\centering
+\input{Traffic_Lights_Controller.tex}
+\vrule
+\input{Traffic_Lights_Register.tex}
+\caption{On the left: The controller agent; On the right: The counter agent}
+\label{fig:tlh}
+\end{figure}
+\begin{figure}
+\centering
+\input{Traffic_Lights_Full.tex}
+\caption{The full traffic lights system}
+\label{fig:tlf}
+\end{figure}
 \end{exi}
@@
 \begin{defi}[Relation under predicate]
-A relation under predicate between states of two automata \(\OA{S_1}{i_1}{J_1}{V_1}{\varphi_1}{T_1}\) and \(\OA{S_2}{i_2}{J_2}{V_2}{\varphi_2}{T_2}\) is a function in \(S_1 \times S_2 \to \rformulae{V_1 \uplus V_2}\).
+A relation under predicate between states of two automata \(\OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(\OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) is a function in \(S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\).
 Two states \(s_1 \in S_1, s_2 \in S_2\) are related under a valuation \(\sigma: V_1 \uplus V_2 \to \values\) iff \(\sigma \vdash R\mpar{s_1, s_2}\).
@@
 \begin{defi}[Simulation on open automata]
-A relation \(\leq\) is a simulation if for any related automata \(\wrel{A_1}{A_2}{R}\) where \(A_1 \defobject \OA{S_1}{i_1}{J_1}{V_1}{\varphi_1}{T_1}\), \(A_2 \defobject \OA{S_2}{i_2}{J_2}{V_2}{\varphi_2}{T_2}\) and \(R: S_1 \times S_2 \to \rformulae{V_1 \uplus V_2}\), \(R\) satisfies both
-\defitem Initial states are related under initial valuations: \(\varphi_1 \uplus \varphi_2 \vdash R\mpar{i_1, i_2}\);
+A relation \(\leq\) is a simulation if for any related automata \(\wrel{A_1}{A_2}{R}\) where \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\), \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and \(R: S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\), \(R\) satisfies both
+\defitem Initial states are related under initial valuations: \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\);
 \defitem From related states, all out-transitions from \(A_1\) can be simulated in \(A_2\) and their target states are related:
@@
 \begin{defi}[Deadlock reduction, intuitive definition]
-A simulation \(\leq\) is deadlock reducing if in all the \(R: S_1 \times S_2 \to \rformulae{V_1 \uplus V_2}\) such that \(\wrel{A_1}{A_2}{R}\), there is one that also satisfies
+A simulation \(\leq\) is deadlock reducing if in all the \(R: S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\) such that \(\wrel{A_1}{A_2}{R}\), there is one that also satisfies
 \begin{multline*}
-	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \sigma: V_1 \uplus V_2 \to \values, \\
-	\mpar{\exists t_2 \in \fOT{s_2}, \sigma \vdash R\mpar{s_1, s_2} \wedge \fguard{t_2}} \implies \bigsymb{\exists} \OTx{2}{}{2}{2} \in T_2, \OTx{1}{}{1}{1} \in T_1, \\
+	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \sigma: V \to \values, \mpar{\sigma \vdash R\mpar{s_1, s_2}} \implies \\
+	\mpar{\forall t_2 \in \fOT{s_2}, \sigma \nvdash \fguard{t_2}} \vee \bigsymb{\exists} \OTx{2}{}{2}{2} \in T_2, \OTx{1}{}{1}{1} \in T_1, \\
 	\sigma \vdash g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_1 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
@@
 \end{defi}
-This definition extends the requirements of a simulation by requiring from the relation that on related states, if there is at least one possible transition in the second automata then there must be a matching possible transition in the first.
+This definition extends the requirements of a simulation by requiring from the relation that on related states, if from a state, a transition is possible in the right automata then on all related states a matching transition is possible in the left automata.
+Equivalently the formulation here is: either there is a possible transition in the first automata matching a possible transition in the second, or there were no possible transition in the second.
 This requirement effectively prevents the presence of deadlock state in the first automaton if there is a related non-deadlock state in the second.
@@
 \begin{defi}[Reachability]
-For any open automata \(A \defobject \OA{S}{i}{V}{\varphi}{J}{T}\), we define the caracterisation of reachable valuations \(\reach{A}: S \to \rformulae{V}\) as the strongest predicate on states such that
-\defitem \(\varphi \vdash \reach{A}\mpar{i}\);
-\defitem \(\forall \OTg \in T, \vdash \reach{A}\mpar{s} \implies \reach{A}\mpar{s'}\psubst{\psi}\).
+For any open automata \(A \defobject \OA{S}{s_0}{V}{\sigma_0}{J}{T}\), we define the caracterisation of reachable valuations \(\reach{A}: S \to \rformulae[V]\) as the strongest predicate on states such that
+\defitem \(\sigma_0 \vdash \reach{A}\mpar{s_0}\);
+\defitem \(\forall \OTg \in T, \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}\).
 \end{defi}
-The caracterisation of reachable valuations is used to caracterise the states and valuations that are reachable in a run of an automaton.
-For a valuation \(\sigma: V \to \values\) and a state \ % TODO HERE
-\begin{defi}[Non-locking composition] % TODO: définir un prédicat d'accessibilité plutôt qu'utiliser un p, faire deux définitions puis un lemme d'équivalence plutôt que def+lem
-The composition \(A_p\subst{A_c}{k} \defobject \OA{S}{i}{V}{\varphi}{J}{T}\) where \(A_c \defobject \OA{S_c}{i_c}{V_c}{\varphi_c}{J_c}{T_c}\), \(k \in J_p\) and \(A_p \defobject \OA{S_p}{i_p}{V_p}{\varphi_p}{J_p}{T_p}\), is a correct composition if there is a predicate on its states \(p: S \to \rformulae{V}\) that satisfies
-\defitem Being valid on initial states under initial valuation: \(\varphi \vdash p\mpar{i}\);
-\defitem Transfering validity across transitions: \(\forall \OTg \in T, \vdash p\mpar{s} \implies p\mpar{s'}\psubst{\psi}\);
-\defitem From states where the predicate is valid, if a transition was possible in \(A_p\) then a transition is possible in \(A\) and the predicate holds in the target state:
-\[ \forall s \in S, \sigma: V \to \values, \mpar{\exists t_p \in \fOT{\pi_{S_p}\mpar{s}}, \sigma \vdash p\mpar{s} \wedge \fguard{t_p}} \implies \bigsymb{\exists} \OTg \in T, \sigma \vdash g \]
+The reachability predicate is used to caracterise the states and valuations that are reachable in a run of an automaton.
+The initial state is reachable in the initial valuation and reachability is preserved by taking valid transitions.
+For a valuation \(\sigma: V \to \values\) and a state \(s \in S\), \(\sigma \vdash \reach{A}\mpar{s}\) iff there is a run of the open automaton which reaches \(s\) with the valuation \(\sigma\).
+Another way to understand this predicate is that it is the least fixpoint of the union of valuations that contains the initial valuation.
+\begin{defi}[Non-locking composition, intuitive definition]
+The composition \(A_p\subst{A_c}{k} \defobject \OA{S}{s_0}{V}{\sigma_0}{J}{T}\) where \(A_c \defobject \OA{S_c}{s_{0c}}{V_c}{\sigma_{0c}}{J_c}{T_c}\), \(k \in J_p\) and \(A_p \defobject \OA{S_p}{s_{0p}}{V_p}{\sigma_{0p}}{J_p}{T_p}\), is a non-locking composition if from reachable states, if a transition was possible in \(A_p\) then a transition is possible in \(A_p\subst{A_c}{k}\):
+\begin{multline*}
+	\forall s \in S, \sigma: V \to \values, \mpar{\sigma \vdash \reach{A_p\subst{A_c}{k}}\mpar{s}} \implies \\
+	\mpar{\forall t_p \in \fOT{\pi_{S_p}\mpar{s}}, \sigma \nvdash \fguard{t_p}} \vee \bigsymb{\exists} \OTg \in T, \sigma \vdash g
+\end{multline*}
 \end{defi}
@@
 
-\begin{lem}
-The formula in the definition of deadlock reduction is equivalent to the following:
+\begin{defi}[Deadlock reduction, working definition]
+A simulation \(\leq\) is deadlock reducing if in all the \(R: S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\) such that \(\wrel{A_1}{A_2}{R}\), there is one that also satisfies
 \[ \forall \mpar{s_1, s_2} \in S_1 \times S_2, \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \]
-\end{lem}
-\begin{proof} Let \(R\) be a witness of the simulation \(A_1 \leq A_2\).
+\end{defi}
+\begin{proof} % Always introduce hypothesis and goals on a big math env, recall definitions (also simulation) and call hypothesis H1, H2, ...
+Let \(R\) be a witness of the simulation \(A_1 \leq A_2\).
 \item[\(\implies\):] If \(R\) satisfies the deadlock reduction definition, let \(\mpar{s_1, s_2} \in S_1 \times S_2\).
@@
 	We can decompose it by admitting the left part of the implication then decomposing the big disjunction to get \(\sigma \vdash R\mpar{s_1, s_2}\) as \hyp{p} and \(t_2 \in \fOT{s_2}\) such that \hyp{g2}: \(\sigma \vdash \fguard{t_2}\).
-	We are left to prove \[ \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{G1} \]
+	We are left to prove \[ \sigma \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{G1} \]
 	To do that we will use the fact that \(R\) satisfies the deadlock reduction definition with the current value of \(s_1, s_2, \sigma\).
@@
 
-\begin{lem}
+\begin{defi}[Non-locking composition, working definition]
+The composition \(A \defobject A_p\subst{A_c}{k}\) is 
 The second part of the formula in the definition of correct composition is equivalent to the following:
 \[ \forall s \in S, \vdash p\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
-\end{lem}
+\end{defi}
 \begin{proof} % TODO HERE
@@
 So looking at restricted cases where holes are related in a specific manner can help understanding the general case.
-For two open automata \(A_1 \defobject \OA{S_1}{i_1}{J_1}{V_1}{\varphi_1}{T_1}\) and \(A_2 \defobject \OA{S_2}{i_2}{J_2}{V_2}{\varphi_2}{T_2}\), the following refinement relations are defined.
+For two open automata \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), the following refinement relations are defined.
 
@@
 If \(J_1 = J_2\) then ``\(A_1\) is a hole-identical refinement of \(A_2\)", noted \(A_1 \leq_= A_2\), is defined as:
-\[ \exists R: \mpar{S_1 \times S_2} \to \rformulae{V_1 \uplus V_2}, \varphi_1 \uplus \varphi_2 \vdash R\mpar{i_1, i_2} \qwedge R \text{ hole-identical simulation of } A_1 \text{ in } A_2 \]
+\[ \exists R: \mpar{S_1 \times S_2} \to \rformulae[V_1 \uplus V_2], \sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}} \qwedge R \text{ hole-identical simulation of } A_1 \text{ in } A_2 \]
 \end{defi}
@@
 This is already used in FH-bisimulation introduced in previous articles about open automata.
-So the meaning of \(\varphi_1 \uplus \varphi_2 \vdash R\mpar{i_1, i_2}\) is that the initial states with the initial valuation are effectively related.
+So the meaning of \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\) is that the initial states with the initial valuation are effectively related.
 \begin{defi}[Hole-identical simulation]
@@
 \begin{proof} Let \(\mpar{s_1, s_2} \in S_1 \times S_2\),
-\item[\(\Rightarrow\):] We admit the up formula as \(H_{def}\), let \(t_1 \defobject \OTx{1}{}{1}{1} \in T_1\) and \(\sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values\) be such that \(H_{source} \defobject \sigma \vdash R\mpar{s_1, s_2} \wedge g_1\).
+\item[\(\implies\):] We admit the up formula as \(H_{def}\), let \(t_1 \defobject \OTx{1}{}{1}{1} \in T_1\) and \(\sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values\) be such that \(H_{source} \defobject \sigma \vdash R\mpar{s_1, s_2} \wedge g_1\).
 	\(H_{def}\) applied to \(t_1\) gives \(\mpar{t_{2x} \defobject \OTx{2}{x}{2x}{1} \in T_2}^{x \in X}\) and the property \(H_{tmp}\) to which we give \(\sigma\) to get
-	\[ H_{smt} \defobject \sigma \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+	\begin{multline*}
+		H_{smt} \defobject \sigma \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \\
+		\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
 			\alpha_1 = \alpha_{2x} \wedge \bigwedge_{j \in J'_1} \beta_{1j} = \beta_{2xj} \\[12pt]
 			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-	\end{array}} \]
+		\end{array}}
+	\end{multline*}
 	Unfolding the definition of \(\sigma \vdash f\) where \(f\) is not a closed formula in \(H_{smt}\) gives an exists that we use to get \nmm{\nu: \biguplus_{x \in X} \fvars{t_{2x}} \to \values} and
@@
 	As a valuation for variables in \(\fvars{t_{2x}}\) we have \(\nu\), so \(H_{target}\mpar{x}\) concludes the proof.
-\item[\(\Leftarrow\):] We admit the bottom formula as \(H_{ref}\), let \(t_1 \defobject \OTx{1}{}{1}{} \in T_1\) % TODO HERE; quantify on all valuations to get t_{2\sigma}
+\item[\(\impliedby\):] We admit the bottom formula as \(H_{ref}\), let \(t_1 \defobject \OTx{1}{}{1}{} \in T_1\) % TODO HERE; quantify on all valuations to get t_{2\sigma}
 \end{proof}
@@
 If \(J_1 \subseteq J_2\) then ``\(A_1\) is a hole-subset refinement of \(A_2\)", noted \(A_1 \leq_\subseteq A_2\) is defined as:
-\[ \exists R: \mpar{S_1 \times S_2} \to \rformulae{V_1 \uplus V_2}, \varphi_1 \uplus \varphi_2 \vdash R\mpar{i_1, i_2} \wedge R \text{ hole-subset simulation of } A_1 \text{ in } A_2 \]
+\[ \exists R: \mpar{S_1 \times S_2} \to \rformulae[V_1 \uplus V_2], \sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}} \wedge R \text{ hole-subset simulation of } A_1 \text{ in } A_2 \]
 \end{defi}
@@
 	\exists R: \mpar{S_1 \times S_2} \to \formulae, \quad \exists f: J_1 \setminus J_2 \to J_2 \setminus J_1, \\
-	\varphi_1 \uplus \varphi_2 \vdash R\mpar{i_1, i_2} \qwedge f\mpar{J_1 \setminus J_2} = J_2 \setminus J_1 \\
+	\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}} \qwedge f\mpar{J_1 \setminus J_2} = J_2 \setminus J_1 \\
 	\wedge R \text{ hole-f-matching simulation of } A_1 \text{ in } A_2
@@
 \begin{defi}[Open automata refinement]
-For any two open automata \(A_1 \defobject \OA{S_1}{i_1}{J_1}{V_1}{\varphi_1}{T_1}\) and \(A_2 \defobject \OA{S_2}{i_2}{J_2}{V_2}{\varphi_2}{T_2}\), ``\(A_1\) is a refinement of \(A_2\)", noted \(A_1 \leq A_2\), is defined as:
+For any two open automata \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), ``\(A_1\) is a refinement of \(A_2\)", noted \(A_1 \leq A_2\), is defined as:
 \begin{multline*}
-	\exists R: \mpar{S_1 \times S_2} \to \rformulae{V_1 \uplus V_2}, \exists f: J_1 \setminus J_2 \to J_2 \setminus J_1, \\
-	\varphi_1 \uplus \varphi_2 \vdash R\mpar{i_1, i_2} \wedge R \text{ f simulation of } A_1 \text{ in } A_2
+	\exists R: \mpar{S_1 \times S_2} \to \rformulae[V_1 \uplus V_2], \exists f: J_1 \setminus J_2 \to J_2 \setminus J_1, \\
+	\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}} \wedge R \text{ f simulation of } A_1 \text{ in } A_2
 \end{multline*}

### 2021-04-23 2021-Refinement/report.tex
Composisiton example fully integrated

@@
 
-An example of term algebra can be Peano integers (zero, variable and successor function), the formulae associated can use equality relation, \(\mathit{sum}\mpar{a, b, c} \defobject a = b + c\) relation and \(\mathit{prod}\mpar{a, b, c} \defobject a = b \times c\) relation.
+An example of term algebra can be Peano integers (zero, variable and successor function), the formulae associated can use equality relation, the sum relation \(\mathit{sum}\mpar{a, b, c} \defobject a = b + c\) and the product relation \(\mathit{prod}\mpar{a, b, c} \defobject a = b \times c\).
 
@@
 \defitem The values \(\values\), which are interpretations of closed terms.
-\defitem The validity relation on closed formulae, \({\vdash} \subseteq \rformulae\).
+\defitem The satisfiability relation on closed formulae, \({\vdash} \subseteq \rformulae\).
 \defitem The substitution in \(e \in E\) of \(x \in \fvars{e}\) by \(t \in \terms\), \(e\subst{t}{x}\).
@@
 The substitutions might give a ill-formed expression; for instance let the terms be integers and pairs with (pointwise) addition, \(\mpar{a + b}\psubst{a \mapsto 7, b \mapsto \mpar{4, 5}}\) is a ill-formed term.
-This can be guarded with the atom \(e\subst{t}{x} \in E\) and \(e\psubst{\psi} \in E\) and it will implicitely be the case, for instance when there is quantification on \(t\) and \(\psi\), to simplify notations.
+This can be guarded with the check \(e\subst{t}{x} \in E\) and \(e\psubst{\psi} \in E\) and it will implicitely be the case, for instance when there is quantification on \(t\) and \(\psi\), to simplify notations.
 
 The interpretation of terms is supposed to be decidable.
-The validity of formulae might not be decidable nor complete nor consistent, however we will pretend like they are because these are really hard problems for logicians that we don't want to deal with.
+The satisfiability of formulae might not be decidable nor complete nor consistent, however we will pretend like they are because these are really hard problems for logicians that we don't want to deal with.
+For instance a formula with quantifiers on variables might not be provable even if it is true for all values of these variables.
 In practise the formulae will be given to a SMT solver and we make sure they have all the previous properties.
+Actually \(\vdash\) is used to separate the external logic and the logic on \(\formulae\).
 
@@
 We suppose that the interpretation of terms is compatible w.r.t.\@ substitution, that is if two terms \(t\), \(t'\) are interpreted with the same value, then replacing \(t\) by \(t'\) in a well-formed expression makes an equivalent well-formed expression.
-In a formula, a quantifier followed by a finite set will be used as a shorthand for the quantification on every variable in the set, for instance \(\forall A, \exists B, P\) with \(A = \mbrc{a_1, \dots, a_\card{A}}, B = \mbrc{b_1, \dots, b_\card{B}}\) means \(\forall a_1, \dots, \forall a_\card{A}, \exists b_1, \dots, \exists b_\card{B}, P\).
-% maybe Valuation as formula /\ var=val
-
-The validity relations will be noted using the classical relational notation \(\vdash f\).
-The precedence of \(\vdash\) is the lowest on the right side and higher than \(\uplus\) on the left side: \(\forall a \, b, a \uplus b \vdash x \wedge y \implies \exists z, P\mpar{x,z}\) is the same as \(\forall a \, b, \mpar{\mpar{a \uplus b} \vdash \mpar{\mpar{x \wedge y} \implies \exists z, P\mpar{x,z}}}\).
-The usual validity of a formula \(f \in \formulae\) is noted \({\vdash f} \defnotation {\vdash \forall \fvars{f}, f}\).
-The usual validity of a formula \(f \in \formulae\) with some fixed valuation \(\sigma: V \to \values\) is noted \({\sigma \vdash f} \defnotation {\vdash \forall \fvars{f\psubst{\sigma}}, f\psubst{\sigma}}\).
-% TODO: remettre en exists?
-faire des LHS plus compliques style forall LHS exists RHS
-% maybe satisfiability with formulas on the LHS (and variabl sets)
-
-From there the expression algebra is fixed.
+\begin{noti}
+\defitem In a formula, a quantifier followed by a finite set will be used as a shorthand for the quantification on every variable in the set:
+\[ \forall \mbrc{a_1, \dots, a_n}, \exists \mbrc{b_1, \dots, b_m}, P \text{ means } \forall a_1, \dots, \forall a_n, \exists b_1, \dots, \exists b_m, P \]
+% Also valuations \(\sigma: V \to \values\) will be used as formulas, the interpretation is as expected the constraint of variable to their associated value: \nmm{\bigwedge_{v \in V} v = \sigma\mpar{v}}.
+\defitem The satisfiability relation will be noted using the classical relational notation \(\vdash f\).
+\defitem The satisfiability of a formula \(f \in \formulae\) under some valuation \(\sigma: V \to \values\) is noted:
+\[ \sigma \vdash f \defnotation \vdash \exists \fvars{f\psubst{\sigma}}, f\psubst{\sigma} \]
+\defitem The satisfiability of a formula \(f \in \formulae\) with some variable set \(V\) as context is noted:
+\[ V \vdash f \defnotation \vdash \forall V, \exists\mpar{\fvars{f} \setminus V}, f \]
+\defitem The precedence of \(\vdash\) is the lowest on the right side and higher than \(\uplus\) on the left side:
+\[ \forall a \, b, a \uplus b \vdash x \wedge y \implies \exists z, P\mpar{x,z} \text{ is the same as } \forall a \, b, \mpar{\mpar{a \uplus b} \vdash \mpar{\mpar{x \wedge y} \implies \exists z, P\mpar{x,z}}} \]
+\end{noti}
 With these common definitions and notations settled, the objects of interest can now be defined.
 \begin{defi}[Open automaton]
-A semantic open automaton is a tuple \(\OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(S\) the set of states, \(s_0 \in S\) the initial state, \(V\) the set of variable names unique to this automaton, \(\sigma_0: V \to \values\) the initial valuation of variables, \(J\) the set of hole names and \(T\) a set of open-transitions.
+A open automaton is a tuple \(\OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(S\) the set of states, \(s_0 \in S\) the initial state, \(V\) the set of variable names unique to this automaton, \(\sigma_0: V \to \values\) the initial valuation of variables, \(J\) the set of hole names and \(T\) a set of open-transitions.
 
@@
 \begin{defi}[Open transition]
-A semantic open transition is a tuple \nmm{\OTg} with \(s, s' \in S\) the source and target states, \(\alpha \in \ractions\) the produced action, \(J' \subseteq J\) the holes involved, \(\beta_j \in \ractions\) the actions of the holes, \(g \in \rformulae[V]\) the guard and \(\psi: V \to \rterms\) the new value of the variables.
+An open transition is a tuple \nmm{\OTg} with \(s, s' \in S\) the source and target states, \(\alpha \in \actions\) the produced action, \(J' \subseteq J\) the holes involved, \(\beta_j \in \actions\) the actions of the holes, \(g \in \rformulae\) the guard and \(\psi: V \to \terms\) the new value of the variables.
 \end{defi}
+An open transition can have many unbound variable, actually any well-formed substitution of the unbound variables of the transition minus the automaton variables is a transition that the open automaton can perform.
+
 The intuition of a semantic open automaton is a partially defined LTS with variables, guards on transitions and parametrised actions.
@@
 The open transitions do not indicate the source and target states since that is the role of the transitions arrows; only the action is on the bottom side of the open transition.
-Also in the example, transitions are specified using variables in place of actions or values.
+Also in the example, transitions are specified using variables in place of actions.
 This is used to represent all the transitions created by a correct substitution of these variables, which cannot be drawn otherwise as there are often infinitly many.
 
-There is a model where open automata have finitely many transitions and variables like that are allowed in any expression, not only as a tool to graphically represent an infinity of transitions but as a real construct.
-This model is the structural open automata as opposed to the model used here of semantic open automata.
-The structural version is more adapted to uses where the object manipulated must be finite, for example in algorithms, whereas the semantic version avoids the manipulation of substitutions, which simplifies proofs.
-
 Let's get back to the example.
-The automata on the left side is \(\OA{\mbrc{L, R}}{L}{\emptyset}{\mbrc{}}{\mbrc{l, r}}{T}\) where transitions in \(T\) are generated by all valid substitution of \(x\) and \(y\) in
+The automata on the left side is \(\OA{\mbrc{L, R}}{L}{\emptyset}{\mbrc{}}{\mbrc{l, r}}{T}\) where transitions in \(T\) are generated by
 \begin{align*}
@@
 \end{align*}
-Note that we could have expressed the transition in the middle with \(\mbrc{l \mapsto \delta\mpar{x}, r \mapsto \act{acc}\mpar{x}}\) wich would have avoided many transitions with trivially false guards like the one where \(x \mapsto 1, y \mapsto 2\) which has the guard \(1 = 2\).
+Note that we could have expressed the transition in the middle with \(\mbrc{l \mapsto \delta\mpar{x}, r \mapsto \act{acc}\mpar{x}}\) which would have avoided many transitions with trivially false guards like the one where \(x \mapsto 1, y \mapsto 2\) which has the guard \(1 = 2\).
 
@@
 The drawing introduces the double arrows which is used to denote the initial valuation.
-The automata drawn is \(\OA{\mbrc{\_}}{\_}{\mbrc{v}}{l^\mbrc{v}}{\mbrc{l, r}}{T}\) where transitions in \(T\) are like previously all the transitions generated by valid substitution of \(x\) and \(y\) in
+The automata drawn is \(\OA{\mbrc{\_}}{\_}{\mbrc{v}}{l^\mbrc{v}}{\mbrc{l, r}}{T}\) where transitions in \(T\) are like previously all the transitions generated by
 \begin{align*}
@@
 The same applies for \(l\).
-\(v\) is a variable name for the automaton and a variable in the guard, but its value is not substituted.
-If an automaton variable \(v\) is in a transition outside of the guard then it would mean that, any transition obtained by valid substitution of \(v\) with a value \(x\) and by adding \(v = x\) to the guard, would be a transition of the automaton.
+\(v\) is a variable name for the automaton and a variable in the guard, so its value is not substituted.
+For instance \nmm{\OT{\_}{\_}{\tau}{\mbrc{l \mapsto \tau}}{v = l \wedge \tau \neq \delta}{\mbrc{}}} is in \(T\) but not \nmm{\OT{\_}{\_}{\tau}{\mbrc{l \mapsto \tau}}{l = l \wedge \tau \neq \delta}{\mbrc{}}} (result of the substitution \(v \mapsto l\)).
 
-% TODO: run the automaton conceptually
+An imaginary run of this open automaton can be the automaton in the hole \(l\) emits many actions, this synchronises with the only transition possible at that moment because \(v = l\).
+Then the automaton in hole \(l\) emits a \(\delta\mpar{t}\), this is synchonised with the action that sets \(v \gets r\) and the automata in hole \(r\) must emit a \(\act{acc}\mpar{t}\).
+Finally the automaton in the hole \(r\) emits any sequence of action.
+
+Another imaginary run can be the automaton in the hole \(l\) emits a sequence of action and the automaton in the hole \(r\) cannot emit a \(\act{acc}\mpar{t}\) so it never runs.
 \end{exi}
@@
 \begin{defi}[Guard, Out-transition]
+Let \(V\) be the variable names of the considered automaton, \(T\) its transitions and \(s\) be one of its states.
 \(\fOT{s}\) are called the out-transitions of \(s\).
@@
 \end{align*}
+\[ \fvars{\OTg} \defnotation \mpar{\fvars{\alpha} \cup \fvars{g} \cup \bigcup_{j \in J'} \fvars{\beta_j} \cup \bigcup_{v \in V} \fvars{\psi\mpar{v}}} \setminus V \]
 \end{defi}
-From this point semantic open automata and open transitions will be called automata and transitions for simplicity.
+From this point open automata and open transitions will be called automata and transitions for simplicity.
 
-\section{Semantic and composition of Open Automata} % This is taken from 2007.10770.pdf
-% TODO: Intro
-
-An open automaton can be partially specified, the partial specification comes from the holes.
-A hole can be filled with an open automaton, this operation is called \Quentin{composition}{Or substitution, or filling, what do you prefer?}.
+\section{Semantic and composition of Open Automata}
+The interpretation of open automata is a partially specified automaton, where the partially specification comming from the holes.
+This specification can be completed by composing automata into holes so it is natural to take a look at the composition process.
+This was already defined on pNets in previous work\marginpar{cite 2007.10770} but never completely formalised on open automata.
+The below definition of composition is a direct translation of composition on pNets for open automata.
 \begin{defi}[Composition of open automata]
@@
 \end{figure}
+This example is derived and adapted from a traffic light controller in a collection of examples for pNets.
+It is supposed to be a single traffic light.
+
+The figure \ref{fig:tls} is the light controller with some synchronisation logic.
+It still takes an unimplemented control circuit in the hole \(C\) which gives the timings and an also unimplemented register in the hole \(R\) to count external \(\act{tick}\) actions.
+The three states are used to remember which colored light is on and this color can be retrieved by the environment by synchronising with the actions \(\act{onXxx}\) if it is not stored externally.
+
+The color switches when the register and the control circuit agree that the time is over.
+The new time limit can be set by the control circuit and the exposed action to the exterior is a \(\tau\).
+
 \begin{figure}
@@
 \end{figure}
+The component we choose to compose in the holes are in figure \ref{fig:tlh}.
+On the left is the controller agent which will be composed in the hole \(C\).
+Its role is to decide the duration before switching the lights.
+This implementation is simply a constant time for each color.
+
+On the right is the register agent which will be composed in the hole \(R\).
+Its role is to get a target, then count ticks until that target is reached, then emit an action with the elapsed time and restart.
+This implementation does exactly that and forbids any extra tick.
+
 \begin{figure}
@@
 \end{figure}
+The composition of the specification on figure \ref{fig:tls} and the agents on figure \ref{fig:tlh} is the automaton on figure \ref{fig:tlf}.
+Unreachable states and transition with unsatisfiable guards are not drawn.
+The result of the composition has 36 states (\(3 \times 2 \times 6\)) but only 6 are reachable from the initial configuration.
+Also satisfiable guards were replaced with simplified equivalent.
+
+The most notable effect of composition are the following transitions (generic and simplified version):
+\begin{itemize}
+\item \nmm{\OT{XS}{XC}{\tau}{\mbrc{}}{\top}{\mbrc{t \gets k, c \gets 0}}} which is the composition of \nmm{\OT{X}{X}{\tau}{\mbrc{C \mapsto \theta\mpar{x}, R \mapsto \act{set}\mpar{x}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{S}{C}{\act{set}\mpar{x}}{\mbrc{}}{\top}{\mbrc{t \gets x, c \gets 0}}} from the register and \nmm{\OT{n}{n+1}{\theta\mpar{k}}{\mbrc{}}{\top}{\mbrc{}}} from the controller.
+\item \nmm{\OT{XC}{XC}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} which is the composition of \nmm{\OT{X}{X}{\act{tick}}{\mbrc{R \mapsto \act{tick}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} from the register.
+\item \nmm{\OT{XC}{ZS}{\act{TurnXxx}}{\mbrc{}}{c = t}{\mbrc{}}} which is the composition of \nmm{\OT{X}{Z}{\act{TurnXxx}}{\mbrc{R \mapsto \act{over}\mpar{x}, C \mapsto \delta\mpar{x}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{C}{S}{\act{over}\mpar{c}}{\mbrc{}}{c = t}{\mbrc{}}} from the register and \nmm{\OT{X}{Z}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} from the controller.
+\end{itemize}
 \end{exi}
@@
 \begin{defi}[Relation under predicate]
-A relation under predicate between states of two automata \(\OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(\OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) is a function in \(S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\).
+A relation under predicate between states of two automata \(\OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(\OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) is a function \(R: S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\).
+
 Two states \(s_1 \in S_1, s_2 \in S_2\) are related under a valuation \(\sigma: V_1 \uplus V_2 \to \values\) iff \(\sigma \vdash R\mpar{s_1, s_2}\).
@@
 	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \sigma: V \to \values, \mpar{\sigma \vdash R\mpar{s_1, s_2}} \implies \\
-	\mpar{\forall t_2 \in \fOT{s_2}, \sigma \nvdash \fguard{t_2}} \vee \bigsymb{\exists} \OTx{2}{}{2}{2} \in T_2, \OTx{1}{}{1}{1} \in T_1, \\
-	\sigma \vdash g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_1 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
+	\mpar{\everymath{\displaystyle}\begin{array}{c}
+		\bigsymb{\exists} \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in T_1 \times T_2, \\
+		\sigma \vdash g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
+	\end{array}} \\
+	\vee \forall t_2 \in \fOT{s_2}, \sigma \nvdash \fguard{t_2}
 \end{multline*}
 \end{defi}
-This definition extends the requirements of a simulation by requiring from the relation that on related states, if from a state, a transition is possible in the right automata then on all related states a matching transition is possible in the left automata.
-Equivalently the formulation here is: either there is a possible transition in the first automata matching a possible transition in the second, or there were no possible transition in the second.
+This definition extends the requirements of a simulation by requiring from the relation that on related states, either there is a pair of possible matching transition or there was no out-transition possible in the specification.
 This requirement effectively prevents the presence of deadlock state in the first automaton if there is a related non-deadlock state in the second.
@@
 
-On the other hand there is a property that we considered for some time, that may arise when designing a refinement relation and that is interesting but actually unwanted:
-\begin{description}
-\item[Daisy equivalence:] \(a\mbrk{D} \leq a \wedge a \leq a\mbrk{D}\), where \(D\) is the single state automaton that can produce any action. % TODO: Find another name
-\end{description}
-This property state that composing a hole with an automaton which can do anything is not a strict refinement.
-While it might seem to be a natural property because this automaton is the closest to the meaning of a hole in term of automaton, there is actually a difference between the two.
-Daisy equivalence allows to refine by filling a hole but also by going the other way, that is creating a hole name and putting its hole action to any transition (and possibly keeping any of the unmodified transitions).
-The unwanted behaviour arise for instance when two independant holes are filled, then a hole is created and its actions are put where the two other actions were.
-This effectively merges independant holes, or equivalently allows to consider that an automaton can be plug simultaneously into several holes which is not part of the composition semantics.
-\begin{exi}
-\end{exi}
+% Decide later to modify or remove it
+% On the other hand there is a property that we considered for some time, that may arise when designing a refinement relation and that is interesting but actually unwanted:
+% \begin{description}
+% \item[Daisy equivalence:] \(a\mbrk{D} \leq a \wedge a \leq a\mbrk{D}\), where \(D\) is the single state automaton that can produce any action. % TODO: Find another name
+% \end{description}
+% This property state that composing a hole with an automaton which can do anything is not a strict refinement.
+% While it might seem to be a natural property because this automaton is the closest to the meaning of a hole in term of automaton, there is actually a difference between the two.
+% Daisy equivalence allows to refine by filling a hole but also by going the other way, that is creating a hole name and putting its hole action to any transition (and possibly keeping any of the unmodified transitions).
+% The unwanted behaviour arise for instance when two independant holes are filled, then a hole is created and its actions are put where the two other actions were.
+% This effectively merges independant holes, or equivalently allows to consider that an automaton can be plug simultaneously into several holes which is not part of the composition semantics.
+% \begin{exi}
+% \end{exi}
 
@@
 For any open automata \(A \defobject \OA{S}{s_0}{V}{\sigma_0}{J}{T}\), we define the caracterisation of reachable valuations \(\reach{A}: S \to \rformulae[V]\) as the strongest predicate on states such that
-\defitem \(\sigma_0 \vdash \reach{A}\mpar{s_0}\);
-\defitem \(\forall \OTg \in T, \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}\).
+\defitem \(\sigma_0 \vdash \reach{A}\mpar{s_0}\).
+\defitem \nmm{\bigsymb{\forall} \OTg \in T, \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}}.
 \end{defi}
+For the reader not used to simulations and bisimulations, this definition with a witness can seem strange.
 The reachability predicate is used to caracterise the states and valuations that are reachable in a run of an automaton.
-The initial state is reachable in the initial valuation and reachability is preserved by taking valid transitions.
-For a valuation \(\sigma: V \to \values\) and a state \(s \in S\), \(\sigma \vdash \reach{A}\mpar{s}\) iff there is a run of the open automaton which reaches \(s\) with the valuation \(\sigma\).
+In fact the role of the witness is to caracterise reachable configurations without having to caracterise the fact that the state and valuation are the result of a valid path in an automaton.
+
+To do that we impose that the initial state is reachable in the initial valuation and that reachability is preserved by taking valid transitions.
+This effectively makes reachability account for all paths, and to not account for impossible path the strongest predicate is used.
 Another way to understand this predicate is that it is the least fixpoint of the union of valuations that contains the initial valuation.
 \begin{defi}[Non-locking composition, intuitive definition]
-The composition \(A_p\subst{A_c}{k} \defobject \OA{S}{s_0}{V}{\sigma_0}{J}{T}\) where \(A_c \defobject \OA{S_c}{s_{0c}}{V_c}{\sigma_{0c}}{J_c}{T_c}\), \(k \in J_p\) and \(A_p \defobject \OA{S_p}{s_{0p}}{V_p}{\sigma_{0p}}{J_p}{T_p}\), is a non-locking composition if from reachable states, if a transition was possible in \(A_p\) then a transition is possible in \(A_p\subst{A_c}{k}\):
+
+The composition resulting in \(A_p\subst{A_c}{k} \defobject \OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(A_c \defobject \OA{S_c}{s_{0c}}{V_c}{\sigma_{0c}}{J_c}{T_c}\), \(A_p \defobject \OA{S_p}{s_{0p}}{V_p}{\sigma_{0p}}{J_p}{T_p}\) and \(k \in J_p\), is a non-locking composition if:
+\defitem From reachable configurations, either a transition is possible in \(A_p\subst{A_c}{k}\) or there were no possible transition in \(A_p\) to begin with
 \begin{multline*}
 	\forall s \in S, \sigma: V \to \values, \mpar{\sigma \vdash \reach{A_p\subst{A_c}{k}}\mpar{s}} \implies \\
-	\mpar{\forall t_p \in \fOT{\pi_{S_p}\mpar{s}}, \sigma \nvdash \fguard{t_p}} \vee \bigsymb{\exists} \OTg \in T, \sigma \vdash g
+	\mpar{\exists t \in T, \sigma \vdash \fguard{t}} \vee \forall t_p \in \fOT{\pi_{S_p}\mpar{s}}, \sigma \nvdash \fguard{t_p}
 \end{multline*}
 \end{defi}
-For the reader not used to simulations and bisimulations, this definition with a witness can seem strange.
-In fact the role of the witness is to caracterise reachable configurations without having to caracterise the fact that the state and valuation are the result of a valid path in an automaton.
-
 When expanding the aliases \(S, i, V\) in the definition, and remarking that the last existential quantifier can be unfolded into a transition in \(A\) and one in \(A_p\) with the added condition that they match, the definition become mildly similar with the deadlock reduction one.
@@
 A simulation \(\leq\) is deadlock reducing if in all the \(R: S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\) such that \(\wrel{A_1}{A_2}{R}\), there is one that also satisfies
-\[ \forall \mpar{s_1, s_2} \in S_1 \times S_2, \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \]
+\[ \forall \mpar{s_1, s_2} \in S_1 \times S_2, \sigma: V_1 \uplus V_2 \to \values, \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \]
 \end{defi}
+\begin{lem}
+The intuitive and working
 \begin{proof} % Always introduce hypothesis and goals on a big math env, recall definitions (also simulation) and call hypothesis H1, H2, ...

### 2021-04-24 2021-Refinement/Composition_deadlock.tex
Locking composition examples

\begin{tikzpicture}

\node[state] (v3) at (0:4) {1C};
\node[state] (v2) at (90:4) {0C};
\node[state,initial] (v1) at (180:4) {0S};
\node[state] (v4) at (270:4) {1S};

\draw  (v1) edge[bend left,looseness=0] node {\OTd{\act{set}\mpar{x}}{}{t \gets x}} (v2);
\draw  (v2) edge[bend left,looseness=0] node {\OTd{\tau}{}{}} (v3);
\draw  (v3) edge[bend left,looseness=0] node[near start] {\OTd{\act{tick}}{}[c < t]{c \gets c + 1}} (v2);
\draw  (v2) edge[bend left,looseness=0] node {\OTd{\act{over}\mpar{c}}{}[c = t]{}} (v1);
\draw  (v1) edge node {\OTd{\tau}{}{}} (v4);

\end{tikzpicture}

### 2021-04-24 2021-Refinement/Composition_nolock.tex
Locking composition examples

\begin{tikzpicture}

\node[state] (v3) at (0:4) {1C};
\node[state] (v2) at (90:4) {0C};
\node[state,initial] (v1) at (180:4) {0S};
\node[state] (v4) at (270:4) {1S};

\draw  (v1) edge[bend left,looseness=0] node {\OTd{\act{set}\mpar{x}}{}{c \gets 0, t \gets x}} (v2);
\draw  (v2) edge[bend left,looseness=0] node {\OTd{\tau}{}{}} (v3);
\draw  (v3) edge[bend left,looseness=0] node[near start] {\OTd{\act{tick}}{}{c \gets c + 1}} (v2);
\draw  (v2) edge[bend left,looseness=0] node {\OTd{\act{over}\mpar{c}}{}[c \geq t]{}} (v1);
\draw  (v1) edge[bend left,looseness=0] node {\OTd{\tau}{}{}} (v4);
\draw  (v4) edge[bend left,looseness=0] node {\OTd{\act{tick}}{}{}} (v1);

\end{tikzpicture}

### 2021-04-24 2021-Refinement/report.tex
Examples corrected and added to report
	modified:   Composition_deadlock.tex
	modified:   Composition_nolock.tex
	modified:   randomtick_clock.tex
	modified:   report.tex

@@
 \begin{multline*}
-	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \sigma: V_1 \uplus V_2 \to \values, \\
-	\bigsymb{\forall} \OTx{1}{}{1}{1} \in T_1, \mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} \OTx{2}{}{2}{2} \in T_2, \\
-	\sigma \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
+	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in T_1, \forall \sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values, \\
+	\mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} t_2 \defobject \OTx{2}{}{2}{2} \in T_2, \exists \nu: \fvars{t_2} \to \values, \\
+	\sigma \uplus \nu \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
 \end{multline*}
 \end{defi}
-The last formula means that for every pair of related states under valuation of the automaton variables and every possible transitions (\(\sigma \vdash g_1\)) from the first automaton, there is a possible transition (\(\sigma \vdash g_2\)) such that the produced action matches (\(\alpha_1 = \alpha_2\)), the holes actions from same hole names (\(J'_1 \cap J'_2\)) match (\(\beta_{1j} = \beta_{2j}\)) and the target states are related after variable update.
+The last formula means that for every pair of related states under valuation of the automaton variables and every possible transitions (\(\vdash g_1\)) from the first automaton, there is a possible transition (\(\vdash g_2\)) such that the produced action matches (\(\alpha_1 = \alpha_2\)), the holes actions from same hole names (\(J'_1 \cap J'_2\)) match (\(\beta_{1j} = \beta_{2j}\)) and the target states are related after variable update.
 This is a natural extenion of the notion of simulation on LTS, which is the same definition without variables and holes and guards.
@@
 \begin{multline*}
-	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \sigma: V \to \values, \mpar{\sigma \vdash R\mpar{s_1, s_2}} \implies \\
+	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V \to \values, \mpar{\sigma \vdash R\mpar{s_1, s_2}} \implies \\
 	\mpar{\everymath{\displaystyle}\begin{array}{c}
-		\bigsymb{\exists} \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in T_1 \times T_2, \\
-		\sigma \vdash g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
+		\bigsymb{\exists} t_1 \defobject \OTx{1}{}{1}{1} \in T_1, t_2 \defobject \OTx{2}{}{2}{2} \in T_2, \exists \nu: \fvars{t_1} \uplus \fvars{t_2} \to \values, \\
+		\sigma \uplus \nu \vdash g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
 	\end{array}} \\
-	\vee \forall t_2 \in \fOT{s_2}, \sigma \nvdash \fguard{t_2}
+	\vee \forall t_2 \in \fOT{s_2}, \forall \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \nvdash \fguard{t_2}
 \end{multline*}
@@
 
-% TODO LATER: livelock and tau-stuttering
+% LATER: livelock and tau-stuttering
 % \item[Livelock reduction:] If \(a \leq b\) then \(a\) does not introduces new livelocks, noted \(a \preceq b\) in the following; % TODO: Find a better place to introduce a better definition of livelock reduction.
@@
 
-% Decide later to modify or remove it
+% LATER: modify or remove it
 % On the other hand there is a property that we considered for some time, that may arise when designing a refinement relation and that is interesting but actually unwanted:
 % \begin{description}
-% \item[Daisy equivalence:] \(a\mbrk{D} \leq a \wedge a \leq a\mbrk{D}\), where \(D\) is the single state automaton that can produce any action. % TODO: Find another name
+% \item[Daisy equivalence:] \(a\mbrk{D} \leq a \wedge a \leq a\mbrk{D}\), where \(D\) is the single state automaton that can produce any action.
 % \end{description}
@@
 \defitem \(\sigma_0 \vdash \reach{A}\mpar{s_0}\).
-\defitem \nmm{\bigsymb{\forall} \OTg \in T, \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}}.
+\defitem \nmm{\bigsymb{\forall} t \defobject \OTg \in T, \forall \nu: \fvars{t} \to \values, \nu \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}}.
 \end{defi}
@@
 \begin{defi}[Non-locking composition, intuitive definition]
-
-The composition resulting in \(A_p\subst{A_c}{k} \defobject \OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(A_c \defobject \OA{S_c}{s_{0c}}{V_c}{\sigma_{0c}}{J_c}{T_c}\), \(A_p \defobject \OA{S_p}{s_{0p}}{V_p}{\sigma_{0p}}{J_p}{T_p}\) and \(k \in J_p\), is a non-locking composition if:
+The composition resulting in \(A_p\subst{A_c}{k} = \OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(A_c \defobject \OA{S_c}{s_{0c}}{V_c}{\sigma_{0c}}{J_c}{T_c}\), \(A_p \defobject \OA{S_p}{s_{0p}}{V_p}{\sigma_{0p}}{J_p}{T_p}\) and \(k \in J_p\), is a non-locking composition if:
 \defitem From reachable configurations, either a transition is possible in \(A_p\subst{A_c}{k}\) or there were no possible transition in \(A_p\) to begin with
 \begin{multline*}
-	\forall s \in S, \sigma: V \to \values, \mpar{\sigma \vdash \reach{A_p\subst{A_c}{k}}\mpar{s}} \implies \\
-	\mpar{\exists t \in T, \sigma \vdash \fguard{t}} \vee \forall t_p \in \fOT{\pi_{S_p}\mpar{s}}, \sigma \nvdash \fguard{t_p}
+	\forall s \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A_p\subst{A_c}{k}}\mpar{s}} \implies \mpar{\exists t \in T, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t}} \\
+	\vee \forall t_p \in \fOT{\pi_{S_p}\mpar{s}}, \forall \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \nvdash \fguard{t_p}
 \end{multline*}
 \end{defi}
+
+\begin{exi}
+\begin{figure}
+\input{randomtick_clock.tex}
+\vrule
+\input{register_anytick.tex}
+\caption{On the left: A clock which imposes a tick; On the right: A modified version of the register at figure \ref{fig:tlh}}
+\label{fig:anytick}
+\end{figure}
+% TODO HERE: explain
+\begin{figure}
+\input{Composition_deadlock.tex}
+\vrule
+\input{Composition_nolock.tex}
+\caption{On the left: Deadlock introduced by composition; On the right: No deadlock introduced by composition}
+\label{fig:deadlock}
+\end{figure}
+% TODO: explain
+\end{exi}
+
 When expanding the aliases \(S, i, V\) in the definition, and remarking that the last existential quantifier can be unfolded into a transition in \(A\) and one in \(A_p\) with the added condition that they match, the definition become mildly similar with the deadlock reduction one.
@@
 A simulation \(\leq\) is deadlock reducing if in all the \(R: S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\) such that \(\wrel{A_1}{A_2}{R}\), there is one that also satisfies
-\[ \forall \mpar{s_1, s_2} \in S_1 \times S_2, \sigma: V_1 \uplus V_2 \to \values, \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \]
+\[ \forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \to \values, \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \]
 \end{defi}
 \begin{lem}
-The intuitive and working
-\begin{proof} % Always introduce hypothesis and goals on a big math env, recall definitions (also simulation) and call hypothesis H1, H2, ...
-Let \(R\) be a witness of the simulation \(A_1 \leq A_2\).
-\item[\(\implies\):] If \(R\) satisfies the deadlock reduction definition, let \(\mpar{s_1, s_2} \in S_1 \times S_2\).
-	The free variables of the equivalent formula are all in \(V_1 \uplus V_2\) so let \(\sigma: V_1 \uplus V_2 \to \values\) be such that
-	\[ \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \]
-	We can decompose it by admitting the left part of the implication then decomposing the big disjunction to get \(\sigma \vdash R\mpar{s_1, s_2}\) as \hyp{p} and \(t_2 \in \fOT{s_2}\) such that \hyp{g2}: \(\sigma \vdash \fguard{t_2}\).
-	We are left to prove \[ \sigma \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{G1} \]
-	To do that we will use the fact that \(R\) satisfies the deadlock reduction definition with the current value of \(s_1, s_2, \sigma\).
-	Now we additionally need to prove \goal{G2}: \(\exists t_2 \in \fOT{s_2}, \sigma \vdash R\mpar{s_1, s_2} \wedge \fguard{t_2}\) before getting hypothesis \hyp{E}:
-	\[ \bigsymb{\exists} \OTx{2}{}{2}{2} \in T_2, \OTx{1}{}{1}{1} \in T_1, \sigma \vdash g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_1 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \]
-	The witness of \goal{G2} is \(t_2\) obtained previously in the big disjunction, and \(\sigma \vdash R\mpar{s_1, s_2} \wedge \fguard{t_2}\) is proved by combining \hyp{p} and \hyp{g2}.
-	Now we can decompose \hyp{E} to get \(t_1 \in T_1\), which we know is also in \(\fOT{s_1}\), a transition that we won't use and \(\sigma \vdash \fguard{t_1}\) which is what we needed to prove the branch \(t_1\) of \goal{G1}.
-\item[\(\impliedby\):] If \(R\) satisfies the equivalent formula, let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \(\sigma: V_1 \uplus V_2 \to \values\).
-	Let admit that there is a transition \(t_2 \in T_2\) such that \hyp{g2}: \(\sigma \vdash R\mpar{s_1, s_2} \wedge \fguard{t_2}\).
-	We need to prove \goal{G1}:
-	\[ \bigsymb{\exists} \OTx{2}{}{2}{2} \in T_2, \OTx{1}{}{1}{1} \in T_1, \sigma \vdash g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_1 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \]
-	We use the fact that \(R\) satisfies the equivalent formula with the current value of \(s_1, s_2\) and \(\sigma\) to get
-	\[ \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \]
-	As this formula is true for all values of each free variable, it is especially true when valuated with \(\sigma\).
-	We know that \(t_2 \in \fOT{s_2}\) so \hyp{g2} proves the left part of that implication and we immediately decompose the right side to get \(t_1 \in \fOT{s_1}\) and \hyp{g1}: \(\fguard{t_1}\).
-
-	We cannot yet prove \goal{G1} because at this point we don't know whether \(t_2\) and \(t_1\) do match.
-	In order to get a matching \(t_2\) we use the fact that \(R\) is also witness of the simulation \(A_1 \leq A_2\) with the current value of \(s_1, s_2, \sigma\) and \(t_1\) as \hyp{sim}:
-	\[ \mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} \OTx{2}{}{2}{2} \in T_2, \sigma \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \]
-	The left part of the implication is the left side of \hyp{g2} so we get \(t'_2 \in T_2\) and what's after as the hypothesis \hyp{target}.
-	The witnesses for \goal{G1} are \(t'_2\) and \(t_1\), and the rest is proved with a combination of \hyp{target} and \hyp{g1}.
-\end{proof}
+The intuitive and working definition of deadlock reduction are equivalent.
+\end{lem}
+Proof is given in the appendix. % TODO: ref
 
 \begin{defi}[Non-locking composition, working definition]
-The composition \(A \defobject A_p\subst{A_c}{k}\) is 
-The second part of the formula in the definition of correct composition is equivalent to the following:
-\[ \forall s \in S, \vdash p\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
+The composition \(A \defobject A_p\subst{A_c}{k}\) is a non-locking composition if:
+\[ \forall s \in S, \forall \sigma: V \to \values, \sigma \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
 \end{defi}
-\begin{proof} % TODO HERE
-\item[\(\implies\):] % TODO
-\item[\(\impliedby\):] % TODO
-\end{proof}
+\begin{lem}
+The intuitive and working definition of non-locking composition are equivalent.
+\end{lem}
+Proof is given in the appendix. % TODO: ref and proof in apendix
+
+% TODO: sufficient condition
+
 From this point and in the previous definitions, composition will only refer to correct composition.
 
-% TODO: Some equivalences
 % ``Composition completeness" can be modified into ``Deadlock reduction completeness" to be compatible with ``Deadlock reduction": \(\forall a\, b, a\mbrk{b} \sqsubseteq a \implies a\mbrk{b} \leq a\).
 % Only the latter will be considered.
-% Similar issues arise on other properties and can be fixed by changing the prerequisites to insure that the most deadlock-prone composition of automata is composition complete:
+% Similar issues arise on other properties and can be fixed by changing the prerequisites to ensure that the most deadlock-prone composition of automata is composition complete:
 % \begin{description}
@@
 
-% Transition: Working definitions next section
+With all these properties we can now look at some concrete refinemet relations.
 
 \section{Preliminary refinement relations}
-The main objective of the refinement relation in this section is to be able to say that a composition of two automata is a refinement of the base automaton (\(a\mbrk{b} \leq a\)).
+The main objective of the refinement relations in this section is to be able to say that a composition of two automata is a refinement of the base automaton (\(a\mbrk{b} \leq a\)).
 However composing an open automaton can give an automaton where not much can be said in terms of hole indicies.
@@
 The goal is to caracterise open automata that have a more determined (more deterministic) behaviour without adding deadlocks.
-\begin{defi}[Hole-identical refinement]
+\begin{defi}[Hole-identical refinement] % TODO: transition variables
 If \(J_1 = J_2\) then ``\(A_1\) is a hole-identical refinement of \(A_2\)", noted \(A_1 \leq_= A_2\), is defined as:
@@
 
+\section{Appendix}
+Proof of lemma 1:
+\begin{proof} % TODO HERE: Always introduce hypothesis and goals on a big math env, recall definitions (also simulation) and call hypothesis H1, H2, ...
+Let \(R, A_1, A_2\) be such that \(\wrel{A_1}{A_2}{R}\).
+We want to prove:
+\begin{gather*}
+	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \to \values, \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \\
+\iff
+	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V \to \values, \mpar{\sigma \vdash R\mpar{s_1, s_2}} \implies \\
+	\mpar{\everymath{\displaystyle}\begin{array}{c}
+		\bigsymb{\exists} t_1 \defobject \OTx{1}{}{1}{1} \in T_1, t_2 \defobject \OTx{2}{}{2}{2} \in T_2, \exists \nu: \fvars{t_1} \uplus \fvars{t_2} \to \values, \\
+		\sigma \uplus \nu \vdash g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
+	\end{array}} \\
+	\vee \forall t_2 \in \fOT{s_2}, \forall \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \nvdash \fguard{t_2}
+\end{gather*}
+\item[\(\implies\):] If \(R\) satisfies the deadlock reduction definition, let \(\mpar{s_1, s_2} \in S_1 \times S_2\).
+	The free variables of the equivalent formula are all in \(V_1 \uplus V_2\) so let \(\sigma: V_1 \uplus V_2 \to \values\) be such that
+	\[ \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \]
+	We can decompose it by admitting the left part of the implication then decomposing the big disjunction to get \(\sigma \vdash R\mpar{s_1, s_2}\) as \hyp{p} and \(t_2 \in \fOT{s_2}\) such that \hyp{g2}: \(\sigma \vdash \fguard{t_2}\).
+	We are left to prove \[ \sigma \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{G1} \]
+	To do that we will use the fact that \(R\) satisfies the deadlock reduction definition with the current value of \(s_1, s_2, \sigma\).
+	Now we additionally need to prove \goal{G2}: \(\exists t_2 \in \fOT{s_2}, \sigma \vdash R\mpar{s_1, s_2} \wedge \fguard{t_2}\) before getting hypothesis \hyp{E}:
+	\[ \bigsymb{\exists} \OTx{2}{}{2}{2} \in T_2, \OTx{1}{}{1}{1} \in T_1, \sigma \vdash g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_1 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \]
+	The witness of \goal{G2} is \(t_2\) obtained previously in the big disjunction, and \(\sigma \vdash R\mpar{s_1, s_2} \wedge \fguard{t_2}\) is proved by combining \hyp{p} and \hyp{g2}.
+	Now we can decompose \hyp{E} to get \(t_1 \in T_1\), which we know is also in \(\fOT{s_1}\), a transition that we won't use and \(\sigma \vdash \fguard{t_1}\) which is what we needed to prove the branch \(t_1\) of \goal{G1}.
+\item[\(\impliedby\):] If \(R\) satisfies the equivalent formula, let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \(\sigma: V_1 \uplus V_2 \to \values\).
+	Let admit that there is a transition \(t_2 \in T_2\) such that \hyp{g2}: \(\sigma \vdash R\mpar{s_1, s_2} \wedge \fguard{t_2}\).
+	We need to prove \goal{G1}:
+	\[ \bigsymb{\exists} \OTx{2}{}{2}{2} \in T_2, \OTx{1}{}{1}{1} \in T_1, \sigma \vdash g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_1 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \]
+	We use the fact that \(R\) satisfies the equivalent formula with the current value of \(s_1, s_2\) and \(\sigma\) to get
+	\[ \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \]
+	As this formula is true for all values of each free variable, it is especially true when valuated with \(\sigma\).
+	We know that \(t_2 \in \fOT{s_2}\) so \hyp{g2} proves the left part of that implication and we immediately decompose the right side to get \(t_1 \in \fOT{s_1}\) and \hyp{g1}: \(\fguard{t_1}\).
+
+	We cannot yet prove \goal{G1} because at this point we don't know whether \(t_2\) and \(t_1\) do match.
+	In order to get a matching \(t_2\) we use the fact that \(R\) is also witness of the simulation \(A_1 \leq A_2\) with the current value of \(s_1, s_2, \sigma\) and \(t_1\) as \hyp{sim}:
+	\[ \mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} \OTx{2}{}{2}{2} \in T_2, \sigma \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \]
+	The left part of the implication is the left side of \hyp{g2} so we get \(t'_2 \in T_2\) and what's after as the hypothesis \hyp{target}.
+	The witnesses for \goal{G1} are \(t'_2\) and \(t_1\), and the rest is proved with a combination of \hyp{target} and \hyp{g1}.
+\end{proof}
+
 \end{document}

### 2021-05-01 2021-Refinement/report.tex
Composition in details

@@
 \section{Notations}
+Notations will be defined with the operator \(\defnotation\) and names are given with the operator \(\defobject\) as follows:
+\begin{align*}
+	notation\_with\_variables & \defnotation notated\_object\_using\_the\_variables \\
+	name & \defobject fully\_defined\_mathematical\_object
+\end{align*}
+
 Throughout this paper, tuples might be noted differently depending on what they represent.
@@
 \begin{defi}[Open automaton]
-A open automaton is a tuple \(\OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(S\) the set of states, \(s_0 \in S\) the initial state, \(V\) the set of variable names unique to this automaton, \(\sigma_0: V \to \values\) the initial valuation of variables, \(J\) the set of hole names and \(T\) a set of open-transitions.
+A open automaton is a tuple \(\OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(S\) the set of states, \(s_0 \in S\) the initial state, \(V\) the set of variable names unique to this automaton, \(\sigma_0: V' \to \values\) the initial valuation of variables where \(V' \subseteq V\), \(J\) the set of hole names and \(T\) a set of open-transitions.
 
@@
 All the possible open transitions, from which transitions in \(T\) are selected, are defined below.
+The initial valuation may be a partial valuation of the variables, if the undefined variables are set before being read this behave like a normal variable.
+If the undefined variable is not set before being read then its value may be any fixed value, the potential use of this construct will be explain in more details in section ???\marginpar{refinement section, hole identical is sufficient for the parametric construct}.
 \begin{defi}[Open transition]
@@
 
-The most notable effect of composition are the following transitions (generic and simplified version):
+The transitions obtained by composition are the following (generic and simplified version):
 \begin{itemize}
@@
 \end{itemize}
+
+Let's look at the \(\tau\) transition from the state \(R\) for a more in depth example on how composition and value passing work.
+The transition in the specification is \nmm{\OT{R}{R}{\tau}{\mbrc{R \mapsto \act{set}\mpar{x}, C \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}.
+The composition makes 12 states from the \(R\) state, these states are in \(\mbrc{R} \times \mbrk{1; 6} \times \mbrc{S, C}\), however only \(\mpar{R, 1, S}\) and \(\mpar{R, 2, C}\) are reachable so we will only consider these two.
+In the figure they are noted \(RS\) and \(RC\).
+The holes \(R\) and \(C\) are filles at the same time so the \(\tau\) transition must synchronise with a transition from both the register and the controller.
+
+In the state \(RC\) the composition makes 2 transition from the \(\tau\) transition with a false guard, let's look at one of them.
+\nmm{\OT{RC}{\mpar{R, 3, C}}{\tau}{\mbrc{}}{\top \wedge \top \wedge c < t \wedge \act{set}\mpar{x} = \act{tick} \wedge \theta\mpar{x} = \delta\mpar{x_C}}{\mbrc{c \gets c + 1}}} is made with \nmm{\OT{2}{3}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} from the controller and \nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} from the register.
+Obviously the guard is false so the it is equivalent to have no transition.
+Also the guard is long and can be simplified.
+In this article the guard and transition are always simplified except for the sake of illustrating a concept that is lost in the simplification as it is the case here.
+We can see that the \(x\) variables from the specification, the controller and the register are in conlict.
+To resolve the conflict we renamed the variables.
+
+In the state \(RS\) the composition makes 1 transition from the \(\tau\) transition; this transition is described before but let's look at the details of the composition.
+% TODO: explain value passing then say that in the register \set{t} wouldn't have worked
 \end{exi}
@@
 
-\begin{exi} % TODO
+\begin{exi} % TODO: Traffic light example
 \end{exi}

### 2021-05-01 2021-Refinement/report.tex
Fixed double bracket

@@
 The transition in the specification is \nmm{\OT{R}{R}{\tau}{\mbrc{R \mapsto \act{set}\mpar{x}, C \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}.
-The composition makes 12 states from the \(R\) state, these states are in \(\mbrc{R} \times \mbrk{1; 6} \times \mbrc{S, C}\), however only \(\mpar{R, 1, S}\) and \(\mpar{R, 2, C}\) are reachable so we will only consider these two.
+The composition makes 12 states from the \(R\) state, these states are in \(\mbrc{R} \times \mdbrk{1; 6} \times \mbrc{S, C}\), however only \(\mpar{R, 1, S}\) and \(\mpar{R, 2, C}\) are reachable so we will only consider these two.
 In the figure they are noted \(RS\) and \(RC\).

### 2021-05-03 2021-Refinement/report.tex
Parellel non-locking composition proof begun

@@
 % transitions between sections
-% Re-read what refinement are used for, LOTOS
-% read CCSL and BIP
 
@@
 \section{Introduction}
-Open automata are used to give an interpretation for open pNets.
-% TODO: expand
+The model of open automata is used to give the semantic of open pNets \cite{2007.10770}.
+Open pNets are not petri nets but an intermediate representation used in the VerCors project to perform verification and model checking \cite{henrio:01252323}.
+Open pNets with the open automaton semantic and equivalence relation introduced in previous work \cite{2007.10770} were sucessfully used to verify BIP and GCM \cite{qin:01823507, ameurboulifa:01526055}.
+However equivalences relations are not sufficient to perform model checking, refinement relations are also used.
+For instance an example of open pNet where equivalence is not sufficient was encountered in ...\marginpar{Paper where the motivating example came up}.
 
-\section{Notations}
+In this article we introduce a refinement relation for open automata. % TODO: expand
+
+We begin in section \ref{sec:notations} by giving some notations used throughout this paper.
+Then there are several sections dedicated to define all the interesting objects and properties:
+In section \ref{sec:def} we give a clean and up to date definition of open automata.
+In section \ref{sec:semcompo} we recall the semantic for open automata and their composition without requiring the use of open pNets.
+In section \ref{sec:proofelts} we adapt the standard properties related to refinement relation from LTS to open automata.
+After that the section \ref{sec:prelref} is dedicated to progressively build a refinement relation.
+Finally the section \ref{sec:refinement} introduces and analyses the refinement relation on open automata.
+
+\section{Notations}\label{sec:notations}
 Notations will be defined with the operator \(\defnotation\) and names are given with the operator \(\defobject\) as follows:
@@
 
-\section{Open Automaton}
+\section{Open Automaton}\label{sec:def}
 To define an open automaton we need some preliminary definitions.
@@
 
+\begin{noti}[Bisimilarity, FH-bisimulation]
+The bisimilarity relation on open automata is noted \(\cong\) and the FH-bisimulation \cite{henrio:01055091} is noted \(\overset{FH}=\).
+\end{noti}
+Note that FH-bisimilarity implies bisimilarity.
+
+To illustrate these definitions let's look at two implementations (figure \ref{fig:enable}) of the LOTOS\marginpar{cite something here} operator enable in the open automata model.
+The enable operator runs its the left hand side agent until it chooses to finish, at which point it produces an action \(\delta\) that is synchronised with the first action of the right hand side agent which must be \(\act{acc}\), then only the latter agent runs.
+During the synchronised action \Quentin{data can be exchanged}{I need to read a little bit more on that; is that a return code?}.
+\begin{exi}[Enable, state-oriented]
 \begin{figure}
@@
 \end{figure}
-To illustrate these definitions let's look at two implementations (figure \ref{fig:enable}) of the LOTOS\marginpar{cite something here} operator enable in the open automata model.
-The enable operator runs its the left hand side agent until it chooses to finish, at which point it produces an action \(\delta\) that is synchronised with the first action of the right hand side agent which must be \(\act{acc}\), then only the latter agent runs.
-During the synchronised action \Quentin{data can be exchanged}{I need to read a little bit more on that; is that a return code?}.
-\begin{exi}[Enable, state-oriented]
 To draw automata, the usual circle for states and simple arrows for transitions convention is used.
@@
 \begin{exi}[Enable, variable-oriented]
-The automata drawn on the right side of the figure is an alternative implementation of the enable operator which has already been proven equivalent in previous work by ...\marginpar{cite sth here}.
+The automata drawn on the right side of the figure is an alternative implementation of the enable operator which is FH-bisimilar.
 The drawing introduces the double arrows which is used to denote the initial valuation.
@@
 Finally we can define some utilitary functions:
-\begin{defi}[Guard, Out-transition]
+\begin{defi}[Guard, Out-transition, Transition variables]
 Let \(V\) be the variable names of the considered automaton, \(T\) its transitions and \(s\) be one of its states.
@@
 
-\section{Semantic and composition of Open Automata}
+\section{Semantic and composition of Open Automata}\label{sec:semcompo}
 The interpretation of open automata is a partially specified automaton, where the partially specification comming from the holes.
 This specification can be completed by composing automata into holes so it is natural to take a look at the composition process.
-This was already defined on pNets in previous work\marginpar{cite 2007.10770} but never completely formalised on open automata.
+This was already defined on pNets in previous work \cite{henrio:01299562} but never completely formalised on open automata.
 The below definition of composition is a direct translation of composition on pNets for open automata.
@@
 \begin{exi}
-\begin{figure}
-\centering
-\input{Traffic_Lights_Spec.tex}
-\caption{The specification of a traffic light system}
-\label{fig:tls}
-\end{figure}
 This example is derived and adapted from a traffic light controller in a collection of examples for pNets.
@@
 
+\begin{figure}
+\centering
+\input{Traffic_Lights_Spec.tex}
+\caption{The specification of a traffic light system}
+\label{fig:tls}
+\end{figure}
 \begin{figure}
@@
 
-\begin{figure}
-\centering
-\input{Traffic_Lights_Full.tex}
-\caption{The full traffic lights system}
-\label{fig:tlf}
-\end{figure}
-The composition of the specification on figure \ref{fig:tls} and the agents on figure \ref{fig:tlh} is the automaton on figure \ref{fig:tlf}.
-Unreachable states and transition with unsatisfiable guards are not drawn.
+The automaton on figure \ref{fig:tlf} is bisimilar to the composition of the specification on figure \ref{fig:tls} and the agents on figure \ref{fig:tlh}.
 The result of the composition has 36 states (\(3 \times 2 \times 6\)) but only 6 are reachable from the initial configuration.
@@
 
+\begin{figure}
+\centering
+\input{Traffic_Lights_Full.tex}
+\caption{The full traffic lights system}
+\label{fig:tlf}
+\end{figure}
 Let's look at the \(\tau\) transition from the state \(R\) for a more in depth example on how composition and value passing work.
@@
 
-In the state \(RC\) the composition makes 2 transition from the \(\tau\) transition with a false guard, let's look at one of them.
+In the state \(RC\) the composition makes 2 transition from the \(\tau\) transition but both have a false guard; let's look at one of them.
 \nmm{\OT{RC}{\mpar{R, 3, C}}{\tau}{\mbrc{}}{\top \wedge \top \wedge c < t \wedge \act{set}\mpar{x} = \act{tick} \wedge \theta\mpar{x} = \delta\mpar{x_C}}{\mbrc{c \gets c + 1}}} is made with \nmm{\OT{2}{3}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} from the controller and \nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} from the register.
@@
 
-In the state \(RS\) the composition makes 1 transition from the \(\tau\) transition; this transition is described before but let's look at the details of the composition.
-% TODO: explain value passing then say that in the register \set{t} wouldn't have worked
+In the state \(RS\) the composition makes 1 transition from the \(\tau\) transition.
+This transition is described before but let's look at the details of the composition.
+The obtained guard is \(\top \wedge \top \wedge \top \wedge \theta\mpar{x} = \theta\mpar{17} \wedge \act{set}\mpar{x} = \act{set}\mpar{x_R}\) and the obtained new values of the variables is \(\mbrc{t \gets x_R, c \gets 0}\).
+We can see here how value passing work: the only possible value of \(x\) and \(x_R\) making the guard hold is \(17\), this value has been synchronised from the controller to \(x\) then to the second occurence of \(x\) to the distinct \(x\) of the register.
+This guard and value update can be simplified to the one shown on the drawing.
+Note that \nmm{\OT{S}{C}{\act{set}\mpar{t}}{\mbrc{}}{\top}{\mbrc{c \gets 0}}} wouldn't have worked as a transition for the controller because \(t\) is fixed before the transition and its value cannot be set outside of the variable update, hence the use of a local variable \(x\).
 \end{exi}
 
-\section{What is a refinement for Open Automata}
+\section{What is a refinement for Open Automata}\label{sec:proofelts}
 There are several properties that we may want from a refinement relation.
@@
 Here the main properties that we want are related to composition and action refinement.
-A suitable kind of refinement relation for this kind of properties is simulation refinement:
-A bisimulation has already been proposed for open automata \marginpar{cite an article here} that is compatible with composition.
+Because of composition, a relation as strong as simulation refinement must be used as observed in the articles about FH-bisimulation \cite{henrio:01055091}.
 
-% THIS WILL BE RE-WRITTEN LATER
-Other kind of refinement relation that \Quentin{I may explore}{This is a note for possible path, some may be explored, some may not.} are control refinement/hole refinement\footnote{No good formulation atm, the idea is that \(a \leq b \defnotation sth \wedge J_a \setminus J_b \leq_{ctrl} J_b \setminus J_a\), sth is probably a clause to ensure that they behave the same without holes involved.}, (meet semi)lattice refinement\footnote{meet = handshake, \(a \leq b \defnotation a = a || b\) with sync holes, I think this will be equivalent to hole-identical sim, (join=non-det choice?)}, weak-simulation refinement\footnote{Weak variation for each interesting simulation refinement}, composition-correct refinement\footnote{Basically a stricter variant of simulation-refinement where simulation has to take place the other way for some transitions (no different holes?) in order to be correct wrt composition}.
+% LATER
+% Other kind of refinement relation that \Quentin{I may explore}{This is a note for possible path, some may be explored, some may not.} are control refinement/hole refinement\footnote{No good formulation atm, the idea is that \(a \leq b \defnotation sth \wedge J_a \setminus J_b \leq_{ctrl} J_b \setminus J_a\), sth is probably a clause to ensure that they behave the same without holes involved.}, (meet semi)lattice refinement\footnote{meet = handshake, \(a \leq b \defnotation a = a || b\) with sync holes, I think this will be equivalent to hole-identical sim, (join=non-det choice?)}, weak-simulation refinement\footnote{Weak variation for each interesting simulation refinement}, composition-correct refinement\footnote{Basically a stricter variant of simulation-refinement where simulation has to take place the other way for some transitions (no different holes?) in order to be correct wrt composition}.
 
@@
 % LATER: livelock and tau-stuttering
-% \item[Livelock reduction:] If \(a \leq b\) then \(a\) does not introduces new livelocks, noted \(a \preceq b\) in the following; % TODO: Find a better place to introduce a better definition of livelock reduction.
-% \defitem \textbf{\(\tau\)-stuttering} iff . % TODO
+% \item[Livelock reduction:] If \(a \leq b\) then \(a\) does not introduces new livelocks, noted \(a \preceq b\) in the following; % Find a better place to introduce a better definition of livelock reduction.
+% \defitem \textbf{\(\tau\)-stuttering} iff .
 
@@
 This effectively makes reachability account for all paths, and to not account for impossible path the strongest predicate is used.
-Another way to understand this predicate is that it is the least fixpoint of the union of valuations that contains the initial valuation.
+Another way of understanding this predicate is that it is the least fixpoint of the union of valuations that contains the initial valuation:
+\begin{align*}
+	f\mpar{p} = s' \mapsto p\mpar{s'} \vee \bigsymb{\bigvee_\subbox{\OTg \,\in\, T}} p\mpar{s}\psubst{\psi} \wedge g &&
+	\reach{A} = \lim_n f^n\mpar{s \mapsto \choice{\sigma_0 & s = s_0 \\ \bot & \text{otherwise}}}
+\end{align*}
+
 \begin{defi}[Non-locking composition, intuitive definition]
@@
 
-\begin{exi}
+To illustrate the introduction of a deadlock in a composition and the definition of non-locking composition, let's look at an example.
+\begin{exi}[Deadlocks introduced by composition]
+% TODO HERE: read CCSL & BIP
 \begin{figure}
@@
 \end{figure}
-% TODO HERE: explain
+% TODO: explain
 \begin{figure}
@@
 \input{Composition_nolock.tex}
-\caption{On the left: Deadlock introduced by composition; On the right: No deadlock introduced by composition}
+\caption{On the left: Deadlocks introduced by composition; On the right: No deadlock introduced by composition}
 \label{fig:deadlock}
@@
 \end{lem}
-Proof is given in the appendix. % TODO: ref
 
@@
 \end{lem}
-Proof is given in the appendix. % TODO: ref and proof in apendix
+Proof of both lemma are given in appendix \ref{apx:lemeqd}.
 
-% TODO: sufficient condition
+% TODO?: sufficient condition
 
-From this point and in the previous definitions, composition will only refer to correct composition.
+This new substitution can replace the standard substitution in the case where only one hole is filled and also in the parallel case:
+\begin{thm}[Parallel non-locking substitution]
+Let \(A, B, C\) be open automata, \(J_A\) the hole names of \(A\) and \(k, l \in J_A\) two distinct hole names.
+\[ A\subst{B}{k}\subst{C}{l} \iff A\subst{C}{l}\subst{B}{k} \]
+\end{thm}
+If we prove that, then they are bisimilar because non-locking composition is a restriction of standard composition.
+\begin{proof}
+Both ways are symmetric so we will only prove one way.
+Let \(s' \defobject \mpar{\mpar{s_A, s_C}, s_B}\) and \(\sigma: V_A \uplus V_C \uplus V_B \to \values\) be respectively a state and a valuation of \(A\subst{C}{l}\subst{B}{k}\).
+We need to prove both:
+\begin{gather}
+	\sigma \vdash \reach{A\subst{C}{l}} \wedge \bigvee_\subbox{t \in \fOT{s_A}} \fguard{t} \implies \bigvee_\subbox{t \in \fOT{s_A, s_C}} \fguard{t} \goal{1} \\
+	\sigma \vdash \reach{A\subst{C}{l}\subst{B}{k}} \wedge \bigvee_\subbox{t \in \fOT{s_A, s_C}} \fguard{t} \implies \bigvee_\subbox{t \in \fOT{s'}} \fguard{t} \goal{2}
+\end{gather}
+\(\mpar{s_A, s_B}\) is a state of \(A\subst{B}{k}\), \(s \defobject \mpar{\mpar{s_A, s_B}, s_C}\) is a state of \(A\subst{B}{k}\subst{C}{l}\) and \(\sigma\) is a valuation of their variables so the following hold by hyptoheses:
+\begin{gather}
+	\sigma \vdash \reach{A\subst{B}{k}} \wedge \bigvee_\subbox{t \in \fOT{s_A}} \fguard{t} \implies \bigvee_\subbox{t \in \fOT{s_A, s_B}} \fguard{t} \hyp{1} \\
+	\sigma \vdash \reach{A\subst{B}{k}\subst{C}{l}} \wedge \bigvee_\subbox{t \in \fOT{s_A, s_B}} \fguard{t} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{2}
+\end{gather}
+By admitting and decomposing the left part of \goal{1} and \goal{2} we get the following:
+\begin{align*}
+	\sigma \vdash \reach{A\subst{C}{l}} & \text{ \hyp{\_}} &
+	t_A \in \fOT{s_A} &&
+	\sigma \vdash \fguard{t_A} \text{ \hyp{2}} \\
+	\sigma \vdash \reach{A\subst{C}{l}\subst{B}{k}} & \text{ \hyp{3}} &
+	t_{AC} \in \fOT{s_A, s_C} &&
+	\sigma \vdash \fguard{t_{AC}} \text{ \hyp{4}}
+\end{align*}
+And now we need to prove:
+\begin{align*}
+	\sigma \vdash \bigvee_\subbox{t \in \fOT{s_A, s_C}} \fguard{t} & \text{ \goal{1'}} &
+	\sigma \vdash \bigvee_\subbox{t \in \fOT{s'}} \fguard{t} & \text{ \goal{2'}}
+\end{align*}
+We use the fact that \(A\subst{C}{l}\subst{B}{k} \cong A\subst{B}{k}\subst{C}{l}\) on \hyp{3} to get: % TODO HERE: Add lemma about reachability implication for composition
+\[ \sigma \vdash \reach{A\subst{B}{k}\subst{C}{l}} \hyp{5} \]
+% TODO
+\end{proof}
+From this point and in the previous definitions, composition will only refer to non-locking composition.
 
@@
 
-\section{Preliminary refinement relations}
-The main objective of the refinement relations in this section is to be able to say that a composition of two automata is a refinement of the base automaton (\(a\mbrk{b} \leq a\)).
-However composing an open automaton can give an automaton where not much can be said in terms of hole indicies.
+\section{Preliminary refinement relations}\label{sec:prelref}
+The main goal of this section is to help the reader understand the problems, constraints and different elements involved to solve them so that they are not all introduced at once in the real refinement relation.
+The main objective of the refinement relations in this section is to be able to say that a composition of two automata is a refinement of the base automaton (\(a\mbrk{b} \leq a\)) in restricted interesting cases.
+Hopefully they can be used as simpler (and less expensive) versions of the real refinement relation in the case the manipulated automata respect the constraints.
+
+Composing an open automaton can give an automaton where not much can be said in terms of hole indicies.
 So looking at restricted cases where holes are related in a specific manner can help understanding the general case.
@@
 
-\section{Refinement relation for open automata}
+\section{Refinement relation for open automata}\label{sec:refinement}
 % meaning of f, what happens depending on f
@@
 
-\section{Appendix}
-Proof of lemma 1:
-\begin{proof} % TODO HERE: Always introduce hypothesis and goals on a big math env, recall definitions (also simulation) and call hypothesis H1, H2, ...
+\pagebreak
+\bibliographystyle{plain}
+\bibliography{biblio}
+
+\pagebreak
+\appendix
+\part*{Appendix}
+
+\section{Proof of equivalent definitions}\label{apx:lemeqd}
+\begin{proof}[Lemma 1] % TODO HERE: Always introduce hypothesis and goals on a big math env, recall definitions (also simulation) and call hypothesis H1, H2, ...
 Let \(R, A_1, A_2\) be such that \(\wrel{A_1}{A_2}{R}\).
@@
 	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \to \values, \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \\
-\iff
+\iff \\
 	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V \to \values, \mpar{\sigma \vdash R\mpar{s_1, s_2}} \implies \\
@@
 
+% TODO
+
 \end{document}

### 2021-05-04 2021-Refinement/report.tex
some proofreading and comments

@@
 For instance \(\forall \mpar{x, y}, \exists \mpar{x', y}, P\) means \(\forall \mpar{x, y}, \exists \mpar{x', y'}, y = y' \wedge P\).
+\Ludo{Strange}{do we really need this interpretation of quantifiers? I find it disturbing}
 
@@
 The latter will only be used when unambiguous; for instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\), but \(\mbrc{\alpha \mapsto 1, \beta \mapsto 2, \gamma \mapsto 3}\) must be represented with one of the two first notation.
+\Ludo{Strange}{ you mean the last notation is forbidden? but isn't it introduced before?}
 The disjoint union of two maps \(\varphi: I \to X\) and \(\psi: J \to Y\) with \(I \cap J = \emptyset\) is \(\varphi \uplus \psi: I \uplus J \to X \cup Y\).
@@
 For a relation \(\wrel{}{}{}\) which uses a property \(P\) to prove that two element are related \(\forall x \, x', x \wrel{}{}{} x' \iff \exists w: P\mpar{x, x'}\), the fact that there is a valid witness \(w: P\mpar{x, x'}\) is noted \(\wrel{x}{x'}{w}\).
+\Ludo{Strange}{not clear: it seems that $w$ is useless  I guess you mean $P$ depend on $w$ but it is not exactly what is written}
 
@@
 An element \(\mpar{l, t} \in \actions\) is noted \(l\mpar{t}\).
-The formulae form at least a first order logic with an equality relation that is not necessarily the equality on \(\terms\).
+The formulae contain at least first order logic terms with an equality relation that is not necessarily \Ludo{?}{restricted to?} the equality on \(\terms\).
 
@@
 The substitutions might give a ill-formed expression; for instance let the terms be integers and pairs with (pointwise) addition, \(\mpar{a + b}\psubst{a \mapsto 7, b \mapsto \mpar{4, 5}}\) is a ill-formed term.
-This can be guarded with the check \(e\subst{t}{x} \in E\) and \(e\psubst{\psi} \in E\) and it will implicitely be the case, for instance when there is quantification on \(t\) and \(\psi\), to simplify notations.
+This can be guarded with the check \(e\subst{t}{x} \in E\) and \(e\psubst{\psi} \in E\) and it will implicitly be the case, for instance when there is quantification on \(t\) and \(\psi\), to simplify notations.
 
@@
 Actually \(\vdash\) is used to separate the external logic and the logic on \(\formulae\).
+
+\Ludo{?}{I do not understand the meaning of the net paragraph: I must have missed something}
 
@@
 
-To illustrate these definitions let's look at two implementations (figure \ref{fig:enable}) of the LOTOS\marginpar{cite something here} operator enable in the open automata model.
-The enable operator runs its the left hand side agent until it chooses to finish, at which point it produces an action \(\delta\) that is synchronised with the first action of the right hand side agent which must be \(\act{acc}\), then only the latter agent runs.
+To illustrate these definitions we consider  two implementations (figure \ref{fig:enable}) of the LOTOS\marginpar{cite something here} operator enable in the open automata model.
+The enable operator runs  the left hand side agent until it chooses to finish, at which point it produces an action \(\delta\) that is synchronised with the first action of the right hand side agent which must be \(\act{acc}\), then only the latter agent runs.
 During the synchronised action \Quentin{data can be exchanged}{I need to read a little bit more on that; is that a return code?}.
+
 \begin{exi}[Enable, state-oriented]
@@
 \end{figure}
-To draw automata, the usual circle for states and simple arrows for transitions convention is used.
+
+Graphical notations for showing automata are as follows.
+Automata are shown in the figure, the usual circle for states and simple arrows for transitions convention is used.
 The initial state is indicated by a double circle.
 States names are indicated inside the circles and transitions labels are drawn near their corresponding arrow.
-
 The open transitions do not indicate the source and target states since that is the role of the transitions arrows; only the action is on the bottom side of the open transition.
 Also in the example, transitions are specified using variables in place of actions.
-This is used to represent all the transitions created by a correct substitution of these variables, which cannot be drawn otherwise as there are often infinitly many.
+This is used to represent all the transitions created by a correct substitution of these variables, which cannot be drawn as there are often infinitely many.
 
-Let's get back to the example.
+We can now explain the enable operator example.
 The automata on the left side is \(\OA{\mbrc{L, R}}{L}{\emptyset}{\mbrc{}}{\mbrc{l, r}}{T}\) where transitions in \(T\) are generated by
@@
 
-This automaton is an implementation of the enable operator because it begins in the state \(L\) where it allows any transition from its hole \(l\) which is not \(\delta\) then synchronises its holes on the same data, effectively allowing a data exchange when it goes into state \(R\), and finally allows any transition from its hole \(r\).
-Only the synchronisation is hidden to the exterior by sending a \(\tau\) which is usually a silent action always allowed, unsynchronised with other holes and passed unmodified.
-Well here \(\tau\) is not always allowed from the holes in the state \(L\) the hole \(r\) cannot emmit it for the sake of simplifying the first example of open automaton.
+This automaton is an implementation of the enable operator because it begins in the state \(L\) where it allows any transition from its hole \(l\) which is not \(\delta\) then the automaton synchronises its holes on the same data, effectively allowing a data exchange when it goes into state \(R\), and finally allows any transition from its hole \(r\).
+We use the standard convention that uses $\tau$ as a non-observable transition, never synchronised with other actions and passed unmodified.
+Here the synchronisation is hidden to the exterior by sending a \(\tau\).
+\Ludo{Well}{avoid informal English in scientific writing} here \(\tau\) is not always allowed from the holes in the state \(L\) the hole \(r\) cannot emit it for the sake of simplifying the first example of open automaton.
 \end{exi}
 \begin{exi}[Enable, variable-oriented]
-The automata drawn on the right side of the figure is an alternative implementation of the enable operator which is FH-bisimilar.
+The automata drawn on the right side of the figure is an alternative implementation of the enable operator which is FH-bisimilar to the previous one\footnote{FH-bisimulation is defined in ~\cite{addcitation}}.
 The drawing introduces the double arrows which is used to denote the initial valuation.
@@
 The same applies for \(l\).
-\(v\) is a variable name for the automaton and a variable in the guard, so its value is not substituted.
+\(v\) is a variable name for the automaton and a variable in the guard, \Ludo{so its value is not substituted}{I do not understand this: it seems to mean that the substitution of v has no effect}.\Ludo{?}{I believe this needs to be explained more clearly, perhaps based on the def 6 below}
 For instance \nmm{\OT{\_}{\_}{\tau}{\mbrc{l \mapsto \tau}}{v = l \wedge \tau \neq \delta}{\mbrc{}}} is in \(T\) but not \nmm{\OT{\_}{\_}{\tau}{\mbrc{l \mapsto \tau}}{l = l \wedge \tau \neq \delta}{\mbrc{}}} (result of the substitution \(v \mapsto l\)).
@@
 \section{Semantic and composition of Open Automata}\label{sec:semcompo}
-The interpretation of open automata is a partially specified automaton, where the partially specification comming from the holes.
+The interpretation of open automata is a partially specified automaton, where the partial specification comes from the holes.
 This specification can be completed by composing automata into holes so it is natural to take a look at the composition process.
 This was already defined on pNets in previous work \cite{henrio:01299562} but never completely formalised on open automata.
-The below definition of composition is a direct translation of composition on pNets for open automata.
+The  definition of composition below is a direct translation of composition on pNets for open automata.
 \begin{defi}[Composition of open automata]
@@
 
-The figure \ref{fig:tls} is the light controller with some synchronisation logic.
-It still takes an unimplemented control circuit in the hole \(C\) which gives the timings and an also unimplemented register in the hole \(R\) to count external \(\act{tick}\) actions.
+\Ludo{Figure \ref{fig:tls} shows}{rephrased: typo} the light controller with some synchronisation logic.
+It  takes an unimplemented control circuit in the hole \(C\) which gives the timings and an also unimplemented register in the hole \(R\) to count external \(\act{tick}\) actions.
 The three states are used to remember which colored light is on and this color can be retrieved by the environment by synchronising with the actions \(\act{onXxx}\) if it is not stored externally.
@@
 \end{figure}
-The component we choose to compose in the holes are in figure \ref{fig:tlh}.
+The component we choose to compose in the holes are in \Ludo{F}{}igure \ref{fig:tlh}.
 On the left is the controller agent which will be composed in the hole \(C\).
@@
 
-The automaton on figure \ref{fig:tlf} is bisimilar to the composition of the specification on figure \ref{fig:tls} and the agents on figure \ref{fig:tlh}.
+The automaton on Figure \ref{fig:tlf} is bisimilar to the composition of the specification on Figure \ref{fig:tls} and the agents on Figure \ref{fig:tlh}.
 The result of the composition has 36 states (\(3 \times 2 \times 6\)) but only 6 are reachable from the initial configuration.
-Also satisfiable guards were replaced with simplified equivalent.
-
-The transitions obtained by composition are the following (generic and simplified version):
+The transitions obtained by composition are the following (generic and simplified version).
+\Ludo{Also satisfiable guards were replaced with simplified equivalent}{moved but a rephrasing may be better}:
 \begin{itemize}

### 2021-05-04 2021-Refinement/report.tex
More comments

@@
 The transitions obtained by composition are the following (generic and simplified version).
-\Ludo{Also satisfiable guards were replaced with simplified equivalent}{moved but a rephrasing may be better}:
+\Ludo{Also satisfiable guards were replaced with simplified equivalent}{moved but a rephrasing may be better: simplified twice?}:
+
+\Ludo{TODO: exlpain X}{}
+
+\Ludo{TODO: express composition in terms of fililng holes like in def 7}{}
+
 \begin{itemize}
-\item \nmm{\OT{XS}{XC}{\tau}{\mbrc{}}{\top}{\mbrc{t \gets k, c \gets 0}}} which is the composition of \nmm{\OT{X}{X}{\tau}{\mbrc{C \mapsto \theta\mpar{x}, R \mapsto \act{set}\mpar{x}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{S}{C}{\act{set}\mpar{x}}{\mbrc{}}{\top}{\mbrc{t \gets x, c \gets 0}}} from the register and \nmm{\OT{n}{n+1}{\theta\mpar{k}}{\mbrc{}}{\top}{\mbrc{}}} from the controller.
+\item \nmm{\OT{XS}{XC}{\tau}{\mbrc{}}{\top}{\mbrc{t \gets k, c \gets 0}}} which is the composition of \nmm{\OT{X}{X}{\tau}{\mbrc{C \mapsto \theta\mpar{x}, R \mapsto \act{set}\mpar{x}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{S}{C}{\act{set}\mpar{x}}{\mbrc{}}{\top}{\mbrc{t \gets x, c \gets 0}}} from the \Ludo{register}{what is the register?
+do you mean counter?} and \nmm{\OT{n}{n+1}{\theta\mpar{k}}{\mbrc{}}{\top}{\mbrc{}}} from \Ludo{the controller}{why is there no $n$ and $n+1$ in the global state?}.
 \item \nmm{\OT{XC}{XC}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} which is the composition of \nmm{\OT{X}{X}{\act{tick}}{\mbrc{R \mapsto \act{tick}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} from the register.
@@
 \end{figure}
-Let's look at the \(\tau\) transition from the state \(R\) for a more in depth example on how composition and value passing work.
+\Ludo{Let's look}{avoid informal english} at the \(\tau\) transition from the state \(R\) for a more in depth example on how composition and value passing work.
 The transition in the specification is \nmm{\OT{R}{R}{\tau}{\mbrc{R \mapsto \act{set}\mpar{x}, C \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}.
-The composition makes 12 states from the \(R\) state, these states are in \(\mbrc{R} \times \mdbrk{1; 6} \times \mbrc{S, C}\), however only \(\mpar{R, 1, S}\) and \(\mpar{R, 2, C}\) are reachable so we will only consider these two.
+\Ludo{confused}{it is not clear in the text when you write about transistions or states : clarify}
+The composition can produce 12 states containing the \(R\) state, these states are in \(\mbrc{R} \times \mdbrk{1; 6} \times \mbrc{S, C}\), however only \(\mpar{R, 1, S}\) and \(\mpar{R, 2, C}\) are reachable so we will only consider these two.
 In the figure they are noted \(RS\) and \(RC\).
-The holes \(R\) and \(C\) are filles at the same time so the \(\tau\) transition must synchronise with a transition from both the register and the controller.
+The holes \(R\) and \(C\) are \Ludo{filles}{active?
+required?} at the same time so the \(\tau\) transition must synchronise with a transition from both the \Ludo{register}{counter?} and the controller.
 
-In the state \(RC\) the composition makes 2 transition from the \(\tau\) transition but both have a false guard; let's look at one of them.
+In the state \(RC\) the composition makes 2 transition \Ludo{from}{be more precise} the \(\tau\) transition but both have a false guard; let's look at one of them.
 \nmm{\OT{RC}{\mpar{R, 3, C}}{\tau}{\mbrc{}}{\top \wedge \top \wedge c < t \wedge \act{set}\mpar{x} = \act{tick} \wedge \theta\mpar{x} = \delta\mpar{x_C}}{\mbrc{c \gets c + 1}}} is made with \nmm{\OT{2}{3}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} from the controller and \nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} from the register.
-Obviously the guard is false so the it is equivalent to have no transition.
-Also the guard is long and can be simplified.
+Obviously the guard is false so  it is equivalent to have no transition.
+Also the guard  can be simplified.
 In this article the guard and transition are always simplified except for the sake of illustrating a concept that is lost in the simplification as it is the case here.
-We can see that the \(x\) variables from the specification, the controller and the register are in conlict.
+We can see that the \(x\) variables from the specification, the controller and the register are in conflict.
 To resolve the conflict we renamed the variables.

### 2021-05-05 2021-Refinement/report.tex
More comments

@@
 
-In the state \(RC\) the composition makes 2 transition \Ludo{from}{be more precise} the \(\tau\) transition but both have a false guard; let's look at one of them.
+In the state \(RC\) the composition makes 2 transition \Ludo{from}{be more precise} the \(\tau\) transition but both have a false guard; \Ludo{Let's look}{avoid informal english} at one of them.
 \nmm{\OT{RC}{\mpar{R, 3, C}}{\tau}{\mbrc{}}{\top \wedge \top \wedge c < t \wedge \act{set}\mpar{x} = \act{tick} \wedge \theta\mpar{x} = \delta\mpar{x_C}}{\mbrc{c \gets c + 1}}} is made with \nmm{\OT{2}{3}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} from the controller and \nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} from the register.
 Obviously the guard is false so  it is equivalent to have no transition.
-Also the guard  can be simplified.
+\Ludo{rest of the paragraph}{why so much discussion on a useless transition? did I miss something?} Also the guard  can be simplified.
 In this article the guard and transition are always simplified except for the sake of illustrating a concept that is lost in the simplification as it is the case here.
@@
 In the state \(RS\) the composition makes 1 transition from the \(\tau\) transition.
-This transition is described before but let's look at the details of the composition.
+This transition is described before but \Ludo{Let's look}{avoid informal english} at the details of the composition.
 The obtained guard is \(\top \wedge \top \wedge \top \wedge \theta\mpar{x} = \theta\mpar{17} \wedge \act{set}\mpar{x} = \act{set}\mpar{x_R}\) and the obtained new values of the variables is \(\mbrc{t \gets x_R, c \gets 0}\).
-We can see here how value passing work: the only possible value of \(x\) and \(x_R\) making the guard hold is \(17\), this value has been synchronised from the controller to \(x\) then to the second occurence of \(x\) to the distinct \(x\) of the register.
-This guard and value update can be simplified to the one shown on the drawing.
+We can see here how value passing works: the only possible value of \(x\) and \(x_R\) making the guard hold is \(17\), this value has been synchronised from the controller to \(x\) then to the second occurrence of \(x\) to the distinct \(x\) of the register.
+This guard and \Ludo{value update}{what do you mean?} can be simplified to the one shown on the drawing.
 Note that \nmm{\OT{S}{C}{\act{set}\mpar{t}}{\mbrc{}}{\top}{\mbrc{c \gets 0}}} wouldn't have worked as a transition for the controller because \(t\) is fixed before the transition and its value cannot be set outside of the variable update, hence the use of a local variable \(x\).
@@
 There are several properties that we may want from a refinement relation.
-Depending on these properties, several kind of refinement may be used.
-For example if we are interested in being able to produce the same sequence of action we may want to use trace set inclusion as a refinement.
+Depending on these properties, several kinds of refinement may be used.
+For example if we are interested in producing the same sequence of actions we may want to use trace set inclusion as a refinement.
 Here the main properties that we want are related to composition and action refinement.
@@
 \defitem \textbf{a preorder} iff it is reflexive and transitive;
-\defitem \textbf{complete w.r.t.\@ composition} iff \(\forall a\, b, a\mbrk{b} \leq a\);
-\defitem \textbf{correct w.r.t.\@ composition} iff \(\forall a\, b, a \leq b \implies \exists c, a \overset{FH}= b\mbrk{c}\);
-\defitem \textbf{context equivalent for composition} iff \(\forall a\, b\, c, a \leq b \implies a\mbrk{c} \leq b\mbrk{c}\);
+\defitem \textbf{\Ludo{complete}{not sure whyy this is called completeness} w.r.t.\@ composition} iff \(\forall a\, b, a\mbrk{b} \leq a\);
+\defitem \textbf{\Ludo{correct}{This eems very difficult to achieve so calling it correctness and implying that the other relations are not interesting is very strong} w.r.t.\@ composition} iff \(\forall a\, b, a \leq b \implies \exists c, a \overset{FH}= b\mbrk{c}\);
+\defitem \textbf{context \Ludo{equivalent}{equivalent is strange here as there is no equivalence as far as I can see} for composition} iff \(\forall a\, b\, c, a \leq b \implies a\mbrk{c} \leq b\mbrk{c}\);
 \defitem \textbf{congruent for composition} iff \(\forall a\, b\, c, a \leq b \implies c\mbrk{a} \leq c\mbrk{b}\);
@@
 Congruence is the refinement being compatible with being composed in the same automaton.
-Compatibility with composition is the two latter at the same time.
+Compatibility with composition is the two latter at the same time \Ludo{?}{(plus transitivity?) it depends what you mean by ``at the same time''}.
 Finally compatibility with FH-bisimulation is the refinement not being able to distinguish two FH-bisimilar automata.

### 2021-05-06 2021-Refinement/report.tex
False theorem evinced, some corrections applied

@@
 
-In this article we introduce a refinement relation for open automata. % TODO: expand
+In this article we introduce a refinement relation for open automata\marginpar{TODO: expand}.
 
@@
 Throughout this paper, tuples might be noted differently depending on what they represent.
-Quantification will be used loosely, any bound name in a quantification means that the object is constrained to have that previous value, and any new name is bound by the quantifier.
-For instance \(\forall \mpar{x, y}, \exists \mpar{x', y}, P\) means \(\forall \mpar{x, y}, \exists \mpar{x', y'}, y = y' \wedge P\).
-\Ludo{Strange}{do we really need this interpretation of quantifiers? I find it disturbing}
 
 Family of values, or equivalently maps will be noted \(\mset{i \mapsto x_i}{i \in I}\), \(\mset{i \gets x_i}{i \in I}\) or \(x_i^{i \in I}\).
-The latter will only be used when unambiguous; for instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\), but \(\mbrc{\alpha \mapsto 1, \beta \mapsto 2, \gamma \mapsto 3}\) must be represented with one of the two first notation.
-\Ludo{Strange}{ you mean the last notation is forbidden? but isn't it introduced before?}
+The latter will only be used when there is a generating expression; for instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\).
+However \(\mbrc{\alpha \mapsto 1, \beta \mapsto 2, \gamma \mapsto 3}\) has no generating expression and is represented with the first notation in a finite context.
 The disjoint union of two maps \(\varphi: I \to X\) and \(\psi: J \to Y\) with \(I \cap J = \emptyset\) is \(\varphi \uplus \psi: I \uplus J \to X \cup Y\).
 
-For a relation \(\wrel{}{}{}\) which uses a property \(P\) to prove that two element are related \(\forall x \, x', x \wrel{}{}{} x' \iff \exists w: P\mpar{x, x'}\), the fact that there is a valid witness \(w: P\mpar{x, x'}\) is noted \(\wrel{x}{x'}{w}\).
-\Ludo{Strange}{not clear: it seems that $w$ is useless  I guess you mean $P$ depend on $w$ but it is not exactly what is written}
+In a formula, a quantifier followed by a finite set will be used as a shorthand for the quantification on every variable in the set:
+\(\forall \mbrc{a_1, \dots, a_n}, \exists \mbrc{b_1, \dots, b_m}, P\) means \(\forall a_1, \dots, \forall a_n, \exists b_1, \dots, \exists b_m, P\).
 
@@
 An element \(\mpar{l, t} \in \actions\) is noted \(l\mpar{t}\).
-The formulae contain at least first order logic terms with an equality relation that is not necessarily \Ludo{?}{restricted to?} the equality on \(\terms\).
+The formulae contain at least first order logic terms with an equality relation.
+This equality relation is not necessarily a syntactic equality (\(2 + 2 \neq 4\) with a syntactic equality) on \(\terms\).
 
@@
 
-\Ludo{?}{I do not understand the meaning of the net paragraph: I must have missed something}
-
-A value \(v\) may be used for keeping a variable state, and then injected in terms for substitution.
-While this is correct when \(\values \subseteq \rterms\), in the other cases this will be used as a shorthand for substitution with any term which can be interpreted as \(v\).
+Values will be used for keeping a variable state, and then injected in terms for substitution.
+This is correct when \(\values \subseteq \rterms\) and we suppose it is the case.
+Otherwise it doesn't invalidates theorem because it can stand as a shorthand for substitution with any term which is interpreted as \(v\).
 We suppose that the interpretation of terms is compatible w.r.t.\@ substitution, that is if two terms \(t\), \(t'\) are interpreted with the same value, then replacing \(t\) by \(t'\) in a well-formed expression makes an equivalent well-formed expression.
-\begin{noti}
-\defitem In a formula, a quantifier followed by a finite set will be used as a shorthand for the quantification on every variable in the set:
-\[ \forall \mbrc{a_1, \dots, a_n}, \exists \mbrc{b_1, \dots, b_m}, P \text{ means } \forall a_1, \dots, \forall a_n, \exists b_1, \dots, \exists b_m, P \]
-% Also valuations \(\sigma: V \to \values\) will be used as formulas, the interpretation is as expected the constraint of variable to their associated value: \nmm{\bigwedge_{v \in V} v = \sigma\mpar{v}}.
+\begin{noti}[Notations for separating external logic and logic on \(\formulae\)]
 \defitem The satisfiability relation will be noted using the classical relational notation \(\vdash f\).
@@
 \begin{defi}[Open automaton]
-A open automaton is a tuple \(\OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(S\) the set of states, \(s_0 \in S\) the initial state, \(V\) the set of variable names unique to this automaton, \(\sigma_0: V' \to \values\) the initial valuation of variables where \(V' \subseteq V\), \(J\) the set of hole names and \(T\) a set of open-transitions.
+A open automaton is a tuple \(\OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(S\) the set of states, \(s_0 \in S\) the initial state, \(V\) the set of variable names unique to this automaton, \(\sigma_0: V' \to \values\) the initial valuation of variables where \(V' \subseteq V\), \(J\) the set of hole names and \(T\) the set of open transitions.
 
@@
 The variable names may clash when considering two automata, in that case we suppose that we can still distinguish the variables in the formulas.
-All the possible open transitions, from which transitions in \(T\) are selected, are defined below.
+% The open transitions will be considered to be a finite set of representative open transitions. Removing this restriction may break some theorems.
 The initial valuation may be a partial valuation of the variables, if the undefined variables are set before being read this behave like a normal variable.
@@
 \end{defi}
-An open transition can have many unbound variable, actually any well-formed substitution of the unbound variables of the transition minus the automaton variables is a transition that the open automaton can perform.
+An open transition can have many unbound variable, actually an effective transition of the automaton is any well-formed substitution of the unbound variables of the transition minus the automaton variables.
+This is used to constrain the infinite branching to be representable, making it possible to reason about.
 
@@
 This automaton is an implementation of the enable operator because it begins in the state \(L\) where it allows any transition from its hole \(l\) which is not \(\delta\) then the automaton synchronises its holes on the same data, effectively allowing a data exchange when it goes into state \(R\), and finally allows any transition from its hole \(r\).
-We use the standard convention that uses $\tau$ as a non-observable transition, never synchronised with other actions and passed unmodified.
-Here the synchronisation is hidden to the exterior by sending a \(\tau\).
-\Ludo{Well}{avoid informal English in scientific writing} here \(\tau\) is not always allowed from the holes in the state \(L\) the hole \(r\) cannot emit it for the sake of simplifying the first example of open automaton.
+We use the standard convention that uses \(\tau\) as a non-observable transition, never synchronised with other actions and passed unmodified.
+This allows the synchronisation of the two holes to be hidden to the exterior by sending a \(\tau\).
+However here \(\tau\) is not always allowed from the holes, for instance in the state \(L\) the hole \(r\) cannot emit it.
+These transition have been omitted for the sake of simplifying the first example of open automaton.
 \end{exi}
+
+Finally we can define some utilitary functions:
+\begin{defi}[Guard, Out-transition, Transition variables]
+Let \(V\) be the variable names of the considered automaton, \(T\) its transitions and \(s\) be one of its states.
+\(\fOT{s}\) are called the out-transitions of \(s\).
+\begin{align*}
+	\fguard{\OTg} & \defnotation g &
+	\fOT{t} & \defnotation \mset{\OTg \in T}{s = t} &
+	\fIT{t} & \defnotation \mset{\OTg \in T}{s' = t}
+\end{align*}
+\[ \fvars{\OTg} \defnotation \mpar{\fvars{\alpha} \cup \fvars{g} \cup \bigcup_{j \in J'} \fvars{\beta_j} \cup \bigcup_{v \in V} \fvars{\psi\mpar{v}}} \setminus V \]
+\end{defi}
+
 \begin{exi}[Enable, variable-oriented]
-The automata drawn on the right side of the figure is an alternative implementation of the enable operator which is FH-bisimilar to the previous one\footnote{FH-bisimulation is defined in ~\cite{addcitation}}.
+The automata drawn on the right side of the figure is an alternative implementation of the enable operator which is FH-bisimilar to the previous one.
 The drawing introduces the double arrows which is used to denote the initial valuation.
@@
 \end{align*}
-Note that in this example \(r\) is a hole name and also a closed term, but not a variable.
-The same applies for \(l\).
-\(v\) is a variable name for the automaton and a variable in the guard, \Ludo{so its value is not substituted}{I do not understand this: it seems to mean that the substitution of v has no effect}.\Ludo{?}{I believe this needs to be explained more clearly, perhaps based on the def 6 below}
-For instance \nmm{\OT{\_}{\_}{\tau}{\mbrc{l \mapsto \tau}}{v = l \wedge \tau \neq \delta}{\mbrc{}}} is in \(T\) but not \nmm{\OT{\_}{\_}{\tau}{\mbrc{l \mapsto \tau}}{l = l \wedge \tau \neq \delta}{\mbrc{}}} (result of the substitution \(v \mapsto l\)).
+Note that in this example \(r\) and \(l\) are a hole names and also closed terms: this is a naming conflict, we do not have \(J \subseteq \rterms\).
+
+The variables of a transition are all the free variables in the expressions minus the auomaton variables.
+For instance \(v\) is a variable name for the automaton which is used in the guard.
+It is not a transituon variable.
+When generating transition without free variables its value is not substituted with a closed term.
+For instance \nmm{\OT{\_}{\_}{\tau}{\mbrc{l \mapsto \tau}}{v = l \wedge \tau \neq \delta}{\mbrc{}}} is a transition generated by the second transition and is in \(T\) but not \nmm{\OT{\_}{\_}{\tau}{\mbrc{l \mapsto \tau}}{l = l \wedge \tau \neq \delta}{\mbrc{}}} (result of the forbidden substitution \(v \mapsto l\)).
 
@@
 
-Finally we can define some utilitary functions:
-\begin{defi}[Guard, Out-transition, Transition variables]
-Let \(V\) be the variable names of the considered automaton, \(T\) its transitions and \(s\) be one of its states.
-\(\fOT{s}\) are called the out-transitions of \(s\).
-\begin{align*}
-	\fguard{\OTg} & \defnotation g &
-	\fOT{s} & \defnotation \mbrc{\OTg \in T}
-\end{align*}
-\[ \fvars{\OTg} \defnotation \mpar{\fvars{\alpha} \cup \fvars{g} \cup \bigcup_{j \in J'} \fvars{\beta_j} \cup \bigcup_{v \in V} \fvars{\psi\mpar{v}}} \setminus V \]
-\end{defi}
 From this point open automata and open transitions will be called automata and transitions for simplicity.
@@
 
-\Ludo{Figure \ref{fig:tls} shows}{rephrased: typo} the light controller with some synchronisation logic.
+Figure \ref{fig:tls} shows the light controller with some synchronisation logic.
 It  takes an unimplemented control circuit in the hole \(C\) which gives the timings and an also unimplemented register in the hole \(R\) to count external \(\act{tick}\) actions.
@@
 \end{figure}
-The component we choose to compose in the holes are in \Ludo{F}{}igure \ref{fig:tlh}.
+The component we choose to compose in the holes are in Figure \ref{fig:tlh}.
 On the left is the controller agent which will be composed in the hole \(C\).
@@
 \defitem \textbf{a preorder} iff it is reflexive and transitive;
-\defitem \textbf{\Ludo{complete}{not sure whyy this is called completeness} w.r.t.\@ composition} iff \(\forall a\, b, a\mbrk{b} \leq a\);
-\defitem \textbf{\Ludo{correct}{This eems very difficult to achieve so calling it correctness and implying that the other relations are not interesting is very strong} w.r.t.\@ composition} iff \(\forall a\, b, a \leq b \implies \exists c, a \overset{FH}= b\mbrk{c}\);
-\defitem \textbf{context \Ludo{equivalent}{equivalent is strange here as there is no equivalence as far as I can see} for composition} iff \(\forall a\, b\, c, a \leq b \implies a\mbrk{c} \leq b\mbrk{c}\);
+\defitem \textbf{correct w.r.t.\@ composition} iff \(\forall a\, b, a\mbrk{b} \leq a\);
+\defitem \textbf{complete w.r.t.\@ composition} iff \(\forall a\, b, a \leq b \implies \exists c, a \overset{FH}= b\mbrk{c}\);
+\defitem \textbf{context refining for composition} iff \(\forall a\, b\, c, a \leq b \implies a\mbrk{c} \leq b\mbrk{c}\);
 \defitem \textbf{congruent for composition} iff \(\forall a\, b\, c, a \leq b \implies c\mbrk{a} \leq c\mbrk{b}\);
@@
 Correctness w.r.t.\@ composition is the fact that a refinement correspond to the left automaton being equivalent to some composition of the right automaton.
-Context equivalence is the refinement being compatible with composition with the same automaton.
+Context refinement is the refinement being compatible with composition of the same automaton.
 Congruence is the refinement being compatible with being composed in the same automaton.
-Compatibility with composition is the two latter at the same time \Ludo{?}{(plus transitivity?) it depends what you mean by ``at the same time''}.
+Compatibility with composition is the conjunction of the two latter (assuming the relation is a preorder).
 Finally compatibility with FH-bisimulation is the refinement not being able to distinguish two FH-bisimilar automata.
@@
 Two states \(s_1 \in S_1, s_2 \in S_2\) are related under a valuation \(\sigma: V_1 \uplus V_2 \to \values\) iff \(\sigma \vdash R\mpar{s_1, s_2}\).
+For a relation \(\wrel{}{}{}\) which uses a relation under predicate to prove that two element are related \(\forall x \, x', x \wrel{}{}{} x' \iff \exists R, P\mpar{R}\), the fact that there is a valid witness \(R\) is noted \(\wrel{x}{x'}{R}\).
 \end{defi}
@@
 \begin{multline*}
-	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in T_1, \forall \sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values, \\
-	\mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} t_2 \defobject \OTx{2}{}{2}{2} \in T_2, \exists \nu: \fvars{t_2} \to \values, \\
+	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \forall \sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values, \\
+	\mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \\
 	\sigma \uplus \nu \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
@@
 	\mpar{\everymath{\displaystyle}\begin{array}{c}
-		\bigsymb{\exists} t_1 \defobject \OTx{1}{}{1}{1} \in T_1, t_2 \defobject \OTx{2}{}{2}{2} \in T_2, \exists \nu: \fvars{t_1} \uplus \fvars{t_2} \to \values, \\
+		\bigsymb{\exists} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_1} \uplus \fvars{t_2} \to \values, \\
 		\sigma \uplus \nu \vdash g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
@@
 \begin{defi}[Reachability]
-For any open automata \(A \defobject \OA{S}{s_0}{V}{\sigma_0}{J}{T}\), we define the caracterisation of reachable valuations \(\reach{A}: S \to \rformulae[V]\) as the strongest predicate on states such that
+For any open automata \(A \defobject \OA{S}{s_0}{V}{\sigma_0}{J}{T}\), a reachability predicate \(\reach{A}: S \to \rformulae[V]\) is a predicate on states such that
 \defitem \(\sigma_0 \vdash \reach{A}\mpar{s_0}\).
@@
 \end{defi}
-For the reader not used to simulations and bisimulations, this definition with a witness can seem strange.
+For the reader not used to simulations and bisimulations, this definition of a predicate can seem strange.
 The reachability predicate is used to caracterise the states and valuations that are reachable in a run of an automaton.
-In fact the role of the witness is to caracterise reachable configurations without having to caracterise the fact that the state and valuation are the result of a valid path in an automaton.
+In fact the role of the predicate is to caracterise potentially reachable configurations without having to caracterise the fact that the state and valuation are the result of a valid path in an automaton.
 
 To do that we impose that the initial state is reachable in the initial valuation and that reachability is preserved by taking valid transitions.
-This effectively makes reachability account for all paths, and to not account for impossible path the strongest predicate is used.
-Another way of understanding this predicate is that it is the least fixpoint of the union of valuations that contains the initial valuation:
+This effectively makes reachability account for all paths and potentially over-approximate the reachable configurations.
+However the exact rechability may not be reprensentable in the formulae, hence the need of potentially over-approximating.
+
+Another way of understanding this predicate is that it is a fixpoint of the union of valuations that contains the initial valuation:
 \begin{align*}
-	f\mpar{p} = s' \mapsto p\mpar{s'} \vee \bigsymb{\bigvee_\subbox{\OTg \,\in\, T}} p\mpar{s}\psubst{\psi} \wedge g &&
-	\reach{A} = \lim_n f^n\mpar{s \mapsto \choice{\sigma_0 & s = s_0 \\ \bot & \text{otherwise}}}
+	f\mpar{p} = s' \mapsto p\mpar{s'} \vee \bigsymb{\bigvee_\subbox{\OTg \,\in\, \fIT{s'}}} p\mpar{s}\psubst{\psi} \wedge g &&
+	\sigma_0 \vdash \reach{A}\mpar{s_0} &&
+	f\mpar{\reach{A}} = \reach{A}
 \end{align*}
@@
 \begin{defi}[Non-locking composition, intuitive definition]
-The composition resulting in \(A_p\subst{A_c}{k} = \OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(A_c \defobject \OA{S_c}{s_{0c}}{V_c}{\sigma_{0c}}{J_c}{T_c}\), \(A_p \defobject \OA{S_p}{s_{0p}}{V_p}{\sigma_{0p}}{J_p}{T_p}\) and \(k \in J_p\), is a non-locking composition if:
-\defitem From reachable configurations, either a transition is possible in \(A_p\subst{A_c}{k}\) or there were no possible transition in \(A_p\) to begin with
+The composition resulting in \(A_p\subst{A_c}{k} = \OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(A_c \defobject \OA{S_c}{s_{0c}}{V_c}{\sigma_{0c}}{J_c}{T_c}\), \(A_p \defobject \OA{S_p}{s_{0p}}{V_p}{\sigma_{0p}}{J_p}{T_p}\) and \(k \in J_p\), is a non-locking composition if there is a rechability predicate such that from reachable configurations, either a transition is possible in \(A_p\subst{A_c}{k}\) or there were no possible transition in \(A_p\) to begin with
 \begin{multline*}
-	\forall s \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A_p\subst{A_c}{k}}\mpar{s}} \implies \mpar{\exists t \in T, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t}} \\
+	\forall s \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A_p\subst{A_c}{k}}\mpar{s}} \implies \mpar{\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t}} \\
 	\vee \forall t_p \in \fOT{\pi_{S_p}\mpar{s}}, \forall \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \nvdash \fguard{t_p}
@@
 \begin{exi}[Deadlocks introduced by composition]
-% TODO HERE: read CCSL & BIP
+% TODO: give a context, a circuit cannot block physical time from progressing
 \begin{figure}
@@
 
-This new substitution can replace the standard substitution in the case where only one hole is filled and also in the parallel case:
-\begin{thm}[Parallel non-locking substitution]
-Let \(A, B, C\) be open automata, \(J_A\) the hole names of \(A\) and \(k, l \in J_A\) two distinct hole names.
-\[ A\subst{B}{k}\subst{C}{l} \iff A\subst{C}{l}\subst{B}{k} \]
-\end{thm}
-If we prove that, then they are bisimilar because non-locking composition is a restriction of standard composition.
-\begin{proof}
-Both ways are symmetric so we will only prove one way.
-Let \(s' \defobject \mpar{\mpar{s_A, s_C}, s_B}\) and \(\sigma: V_A \uplus V_C \uplus V_B \to \values\) be respectively a state and a valuation of \(A\subst{C}{l}\subst{B}{k}\).
-We need to prove both:
-\begin{gather}
-	\sigma \vdash \reach{A\subst{C}{l}} \wedge \bigvee_\subbox{t \in \fOT{s_A}} \fguard{t} \implies \bigvee_\subbox{t \in \fOT{s_A, s_C}} \fguard{t} \goal{1} \\
-	\sigma \vdash \reach{A\subst{C}{l}\subst{B}{k}} \wedge \bigvee_\subbox{t \in \fOT{s_A, s_C}} \fguard{t} \implies \bigvee_\subbox{t \in \fOT{s'}} \fguard{t} \goal{2}
-\end{gather}
-\(\mpar{s_A, s_B}\) is a state of \(A\subst{B}{k}\), \(s \defobject \mpar{\mpar{s_A, s_B}, s_C}\) is a state of \(A\subst{B}{k}\subst{C}{l}\) and \(\sigma\) is a valuation of their variables so the following hold by hyptoheses:
-\begin{gather}
-	\sigma \vdash \reach{A\subst{B}{k}} \wedge \bigvee_\subbox{t \in \fOT{s_A}} \fguard{t} \implies \bigvee_\subbox{t \in \fOT{s_A, s_B}} \fguard{t} \hyp{1} \\
-	\sigma \vdash \reach{A\subst{B}{k}\subst{C}{l}} \wedge \bigvee_\subbox{t \in \fOT{s_A, s_B}} \fguard{t} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{2}
-\end{gather}
-By admitting and decomposing the left part of \goal{1} and \goal{2} we get the following:
-\begin{align*}
-	\sigma \vdash \reach{A\subst{C}{l}} & \text{ \hyp{\_}} &
-	t_A \in \fOT{s_A} &&
-	\sigma \vdash \fguard{t_A} \text{ \hyp{2}} \\
-	\sigma \vdash \reach{A\subst{C}{l}\subst{B}{k}} & \text{ \hyp{3}} &
-	t_{AC} \in \fOT{s_A, s_C} &&
-	\sigma \vdash \fguard{t_{AC}} \text{ \hyp{4}}
-\end{align*}
-And now we need to prove:
-\begin{align*}
-	\sigma \vdash \bigvee_\subbox{t \in \fOT{s_A, s_C}} \fguard{t} & \text{ \goal{1'}} &
-	\sigma \vdash \bigvee_\subbox{t \in \fOT{s'}} \fguard{t} & \text{ \goal{2'}}
-\end{align*}
-We use the fact that \(A\subst{C}{l}\subst{B}{k} \cong A\subst{B}{k}\subst{C}{l}\) on \hyp{3} to get: % TODO HERE: Add lemma about reachability implication for composition
-\[ \sigma \vdash \reach{A\subst{B}{k}\subst{C}{l}} \hyp{5} \]
-% TODO
-\end{proof}
+This new substitution can replace the standard substitution in the case where only one hole is filled and also in the parallel case.
+In the parallel case the condition is checked after the parallel substitution because there is no guarantee that any order of sequential composition is non-locking for every substitution even if the parallel substitution is non-locking:
+\begin{exi}
+An example of non-locking parallel substitution where no individual substitution is non-locking is given % TODO HERE
+\end{exi}
 From this point and in the previous definitions, composition will only refer to non-locking composition.
@@
 \begin{defi}[Hole-identical simulation]
-\Quentin{``\(R\) is a hole-identical simulation of \(A_1\) in \(A_2\)"}{Any idea on how to note that?
-\(R \vDash A_1 \leq_= A_2\) for instance.} is defined as: % TODO: faire des macros, + A_1 \overset{=}\leq_R A_2
+\Quentin{``\(R\) is a hole-identical simulation of \(A_1\) in \(A_2\)"}{Any idea on how to note that? \(R \vDash A_1 \leq_= A_2\) for instance.} is defined as: % TODO: \wrel
 \begin{multline*}
@@
 	\mpar{\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{} \in T_2}^{x \in X}, \\[12pt]
+		\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{} \in \fOT{s_2}}^{x \in X}, \\[12pt]
 		\forall \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\
@@
 \mpar{\everymath{\displaystyle}\begin{array}{l}
-	\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{} \in T_2}^{x \in X}, \\[12pt]
+	\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{} \in \fOT{s_2}}^{x \in X}, \\[12pt]
 	\forall \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\
@@
 \mpar{\everymath{\displaystyle}\begin{array}{l}
-	\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in T_1, \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\[6pt]
-	\quad \mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} \OTx{2}{}{2}{2} \in T_2, \\[12pt]
+	\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\[6pt]
+	\quad \mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} \OTx{2}{}{2}{2} \in \fOT{s_2}, \\[12pt]
 	\qquad \sigma \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
@@
 \begin{proof} Let \(\mpar{s_1, s_2} \in S_1 \times S_2\),
-\item[\(\implies\):] We admit the up formula as \(H_{def}\), let \(t_1 \defobject \OTx{1}{}{1}{1} \in T_1\) and \(\sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values\) be such that \(H_{source} \defobject \sigma \vdash R\mpar{s_1, s_2} \wedge g_1\).
-	\(H_{def}\) applied to \(t_1\) gives \(\mpar{t_{2x} \defobject \OTx{2}{x}{2x}{1} \in T_2}^{x \in X}\) and the property \(H_{tmp}\) to which we give \(\sigma\) to get
+\item[\(\implies\):] We admit the up formula as \(H_{def}\), let \(t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}\) and \(\sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values\) be such that \(H_{source} \defobject \sigma \vdash R\mpar{s_1, s_2} \wedge g_1\).
+	\(H_{def}\) applied to \(t_1\) gives \(\mpar{t_{2x} \defobject \OTx{2}{x}{2x}{1} \in \fOT{s_2}}^{x \in X}\) and the property \(H_{tmp}\) to which we give \(\sigma\) to get
 	\begin{multline*}
@@
 	\mpar{\renewcommand\arraystretch{1.4}\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} \OTx{1}{}{1}{1} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in T_2}^{x \in X}, \\
+		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
 		\mpar{\forall x \in X, J'_1 = J'_{2x} \cap J_1} \wedge \forall \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\
@@
 	\mpar{\renewcommand\arraystretch{1.4}\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} \OTx{1}{}{1}{1} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in T_2}^{x \in X}, \\
+		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
 		\mpar{\forall x \in X, J'_1 \cap J_2 = J'_{2x} \cap J_1 \wedge f\mpar{J'_1 \setminus J_2} \subseteq J'_{2x}} \wedge \forall \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\
@@
 	\mpar{\renewcommand\arraystretch{1.4}\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} \OTx{1}{}{1}{1} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in T_1}^{x \in X}, \\
+		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_1}}^{x \in X}, \\
 		\mpar{\forall x \in X, J'_1 \cap J_2 = J'_{2x} \cap J_1 \wedge f\mpar{J'_1 \setminus J_2} \subseteq J'_{2x}} \wedge \forall \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\

### 2021-05-06 2021-Refinement/report.tex
Added meeting TODOS

@@
 
-To illustrate these definitions we consider  two implementations (figure \ref{fig:enable}) of the LOTOS\marginpar{cite something here} operator enable in the open automata model.
+To illustrate these definitions we consider  two implementations (figure \ref{fig:enable}) of the LOTOS \cite{ISOLOTOS} operator enable in the open automata model.
 The enable operator runs  the left hand side agent until it chooses to finish, at which point it produces an action \(\delta\) that is synchronised with the first action of the right hand side agent which must be \(\act{acc}\), then only the latter agent runs.
@@
 
-\begin{figure}
+\begin{figure} % TODO: consistency on register and counter, make number appear in the full composed, Change C so that is it not both a state and a hole
 \centering
@@
 \Ludo{Also satisfiable guards were replaced with simplified equivalent}{moved but a rephrasing may be better: simplified twice?}:
+% TODO: explain what you simplified
 
-\Ludo{TODO: exlpain X}{}
+\Ludo{TODO: exlpain X}{} % TODO: generic = XXX stands for Red Green or Yellow
 
@@
 In the state \(RC\) the composition makes 2 transition \Ludo{from}{be more precise} the \(\tau\) transition but both have a false guard; \Ludo{Let's look}{avoid informal english} at one of them.
+% TODO: Insist on the fact that it shows many usefull states and mechanisms and why it is useless
 \nmm{\OT{RC}{\mpar{R, 3, C}}{\tau}{\mbrc{}}{\top \wedge \top \wedge c < t \wedge \act{set}\mpar{x} = \act{tick} \wedge \theta\mpar{x} = \delta\mpar{x_C}}{\mbrc{c \gets c + 1}}} is made with \nmm{\OT{2}{3}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} from the controller and \nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} from the register.
@@
 We can see here how value passing works: the only possible value of \(x\) and \(x_R\) making the guard hold is \(17\), this value has been synchronised from the controller to \(x\) then to the second occurrence of \(x\) to the distinct \(x\) of the register.
-This guard and \Ludo{value update}{what do you mean?} can be simplified to the one shown on the drawing.
+This guard and \Ludo{value update}{what do you mean?} can be simplified to the one shown on the drawing. % TODO: Variable assignment
 Note that \nmm{\OT{S}{C}{\act{set}\mpar{t}}{\mbrc{}}{\top}{\mbrc{c \gets 0}}} wouldn't have worked as a transition for the controller because \(t\) is fixed before the transition and its value cannot be set outside of the variable update, hence the use of a local variable \(x\).

### 2021-05-06 2021-Refinement/report.tex
All comment processed

--- 2021-05-06 2021-Refinement/report.tex
@@
 
-We can now explain the enable operator example.
+We can proceed to explain the left enable operator example.
 The automata on the left side is \(\OA{\mbrc{L, R}}{L}{\emptyset}{\mbrc{}}{\mbrc{l, r}}{T}\) where transitions in \(T\) are generated by
@@
 \(\fOT{s}\) are called the out-transitions of \(s\).
+\(\fIT{s'}\) are called the in-transitions of \(s'\).
 \begin{align*}
-	\fguard{\OTg} & \defnotation g &
 	\fOT{t} & \defnotation \mset{\OTg \in T}{s = t} &
-	\fIT{t} & \defnotation \mset{\OTg \in T}{s' = t}
+	\fIT{t} & \defnotation \mset{\OTg \in T}{s' = t} \\
 \end{align*}
-\[ \fvars{\OTg} \defnotation \mpar{\fvars{\alpha} \cup \fvars{g} \cup \bigcup_{j \in J'} \fvars{\beta_j} \cup \bigcup_{v \in V} \fvars{\psi\mpar{v}}} \setminus V \]
+\begin{gather*}
+	\fvars{\OTg} \defnotation \mpar{\fvars{\alpha} \cup \fvars{g} \cup \bigcup_{j \in J'} \fvars{\beta_j} \cup \bigcup_{v \in V} \fvars{\psi\mpar{v}}} \setminus V \\
+	\fguard{\OTg} \defnotation g
+\end{gather*}
 \end{defi}
@@
 Figure \ref{fig:tls} shows the light controller with some synchronisation logic.
-It  takes an unimplemented control circuit in the hole \(C\) which gives the timings and an also unimplemented register in the hole \(R\) to count external \(\act{tick}\) actions.
-The three states are used to remember which colored light is on and this color can be retrieved by the environment by synchronising with the actions \(\act{onXxx}\) if it is not stored externally.
+It  takes an unimplemented control circuit in the hole \(ctl\) which gives the timings and an also unimplemented counter in the hole \(cnt\) to count external \(\act{tick}\) actions.
+The three states are used to remember which colored light is on and this color can be retrieved by the environment by synchronising with the actions \(\act{onXxx}\) (Xxx is either Red, Yellow or Green) if it is not stored externally.
 
@@
 The component we choose to compose in the holes are in Figure \ref{fig:tlh}.
-On the left is the controller agent which will be composed in the hole \(C\).
+On the left is the controller agent which will be composed in the hole \(ctl\).
 Its role is to decide the duration before switching the lights.
@@
 
-On the right is the register agent which will be composed in the hole \(R\).
+On the right is the counter agent which will be composed in the hole \(cnt\).
 Its role is to get a target, then count ticks until that target is reached, then emit an action with the elapsed time and restart.
@@
 The result of the composition has 36 states (\(3 \times 2 \times 6\)) but only 6 are reachable from the initial configuration.
-The transitions obtained by composition are the following (generic and simplified version).
-\Ludo{Also satisfiable guards were replaced with simplified equivalent}{moved but a rephrasing may be better: simplified twice?}:
-
-\Ludo{TODO: exlpain X}{}
-
-\Ludo{TODO: express composition in terms of fililng holes like in def 7}{}
-
+The transitions obtained by composition were simplified to give the following (where \(n, n+1\) stands for numbers between 1 and 6 and Xxx is either Red, Yellow or Green):
 \begin{itemize}
-\item \nmm{\OT{XS}{XC}{\tau}{\mbrc{}}{\top}{\mbrc{t \gets k, c \gets 0}}} which is the composition of \nmm{\OT{X}{X}{\tau}{\mbrc{C \mapsto \theta\mpar{x}, R \mapsto \act{set}\mpar{x}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{S}{C}{\act{set}\mpar{x}}{\mbrc{}}{\top}{\mbrc{t \gets x, c \gets 0}}} from the \Ludo{register}{what is the register?
-do you mean counter?} and \nmm{\OT{n}{n+1}{\theta\mpar{k}}{\mbrc{}}{\top}{\mbrc{}}} from \Ludo{the controller}{why is there no $n$ and $n+1$ in the global state?}.
-\item \nmm{\OT{XC}{XC}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} which is the composition of \nmm{\OT{X}{X}{\act{tick}}{\mbrc{R \mapsto \act{tick}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} from the register.
-\item \nmm{\OT{XC}{ZS}{\act{TurnXxx}}{\mbrc{}}{c = t}{\mbrc{}}} which is the composition of \nmm{\OT{X}{Z}{\act{TurnXxx}}{\mbrc{R \mapsto \act{over}\mpar{x}, C \mapsto \delta\mpar{x}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{C}{S}{\act{over}\mpar{c}}{\mbrc{}}{c = t}{\mbrc{}}} from the register and \nmm{\OT{X}{Z}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} from the controller.
+\item \nmm{\OT{XnS}{X(n+1)C}{\tau}{\mbrc{}}{\top}{\mbrc{t \gets k, c \gets 0}}} which is the composition of \nmm{\OT{X}{X}{\tau}{\mbrc{ctl \mapsto \theta\mpar{x}, cnt \mapsto \act{set}\mpar{x}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{S}{C}{\act{set}\mpar{x}}{\mbrc{}}{\top}{\mbrc{t \gets x, c \gets 0}}} from the counter and \nmm{\OT{n}{n+1}{\theta\mpar{k}}{\mbrc{}}{\top}{\mbrc{}}} from the controller.
+\item \nmm{\OT{XnC}{XnC}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} which is the composition of \nmm{\OT{X}{X}{\act{tick}}{\mbrc{cnt \mapsto \act{tick}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} from the counter.
+\item \nmm{\OT{YnC}{X(n+1)S}{\act{TurnXxx}}{\mbrc{}}{c = t}{\mbrc{}}} which is the composition of \nmm{\OT{Y}{X}{\act{TurnXxx}}{\mbrc{cnt \mapsto \act{over}\mpar{x}, ctl \mapsto \delta\mpar{x}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{C}{S}{\act{over}\mpar{c}}{\mbrc{}}{c = t}{\mbrc{}}} from the counter and \nmm{\OT{n}{n+1}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} from the controller.
 \end{itemize}
@@
 \end{figure}
-\Ludo{Let's look}{avoid informal english} at the \(\tau\) transition from the state \(R\) for a more in depth example on how composition and value passing work.
-The transition in the specification is \nmm{\OT{R}{R}{\tau}{\mbrc{R \mapsto \act{set}\mpar{x}, C \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}.
-\Ludo{confused}{it is not clear in the text when you write about transistions or states : clarify}
-The composition can produce 12 states containing the \(R\) state, these states are in \(\mbrc{R} \times \mdbrk{1; 6} \times \mbrc{S, C}\), however only \(\mpar{R, 1, S}\) and \(\mpar{R, 2, C}\) are reachable so we will only consider these two.
-In the figure they are noted \(RS\) and \(RC\).
-The holes \(R\) and \(C\) are \Ludo{filles}{active?
-required?} at the same time so the \(\tau\) transition must synchronise with a transition from both the \Ludo{register}{counter?} and the controller.
+To illustrate composition, simplification and value passing, the \(\tau\) transition from the state \(R\) will be examined.
+The transition in the specification is \nmm{\OT{R}{R}{\tau}{\mbrc{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}.
+The composition can produce 12 states containing the \(R\) state, these states are in \(\mbrc{R} \times \mdbrk{1; 6} \times \mbrc{S, C}\), however only \(R1S\) and \(R2C\) are reachable so we will only consider \(\tau\) transitions from these two.
+The holes \(cnt\) and \(ctl\) are both involved in the \(\tau\) transition and filled with automata so the composed automata must synchronise with a transition.
 
-In the state \(RC\) the composition makes 2 transition \Ludo{from}{be more precise} the \(\tau\) transition but both have a false guard; \Ludo{Let's look}{avoid informal english} at one of them.
-\nmm{\OT{RC}{\mpar{R, 3, C}}{\tau}{\mbrc{}}{\top \wedge \top \wedge c < t \wedge \act{set}\mpar{x} = \act{tick} \wedge \theta\mpar{x} = \delta\mpar{x_C}}{\mbrc{c \gets c + 1}}} is made with \nmm{\OT{2}{3}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} from the controller and \nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} from the register.
-Obviously the guard is false so  it is equivalent to have no transition.
-\Ludo{rest of the paragraph}{why so much discussion on a useless transition? did I miss something?} Also the guard  can be simplified.
-In this article the guard and transition are always simplified except for the sake of illustrating a concept that is lost in the simplification as it is the case here.
-We can see that the \(x\) variables from the specification, the controller and the register are in conflict.
-To resolve the conflict we renamed the variables.
+In the state \(R2C\) the composition produces 2 transition by composition out of the \(\tau\) transition but both have a false guard; It is still interesting to look at one of them to show the product of composition without simplification.
 
-In the state \(RS\) the composition makes 1 transition from the \(\tau\) transition.
-This transition is described before but \Ludo{Let's look}{avoid informal english} at the details of the composition.
-The obtained guard is \(\top \wedge \top \wedge \top \wedge \theta\mpar{x} = \theta\mpar{17} \wedge \act{set}\mpar{x} = \act{set}\mpar{x_R}\) and the obtained new values of the variables is \(\mbrc{t \gets x_R, c \gets 0}\).
-We can see here how value passing works: the only possible value of \(x\) and \(x_R\) making the guard hold is \(17\), this value has been synchronised from the controller to \(x\) then to the second occurrence of \(x\) to the distinct \(x\) of the register.
-This guard and \Ludo{value update}{what do you mean?} can be simplified to the one shown on the drawing.
-Note that \nmm{\OT{S}{C}{\act{set}\mpar{t}}{\mbrc{}}{\top}{\mbrc{c \gets 0}}} wouldn't have worked as a transition for the controller because \(t\) is fixed before the transition and its value cannot be set outside of the variable update, hence the use of a local variable \(x\).
+\nmm{\OT{R2C}{R3C}{\tau}{\mbrc{}}{\top \wedge \top \wedge c < t \wedge \act{set}\mpar{x} = \act{tick} \wedge \theta\mpar{x} = \delta\mpar{x_C}}{\mbrc{c \gets c + 1}}} is made with \nmm{\OT{2}{3}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} from the controller and \nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} from the counter.
+Obviously the equality of actions in the guard cannot be satisfied so the guard is false, it is equivalent to have no transition.
+We could go on to another transition but something worth explaining happened to build its guard.
+The first two \(\top\) come from the guards of the specification and the controller.
+\(c < t\) comes from the counter.
+The rest of the guard comes from the equality constraint between holes actions and automata actions.
+When composing this expression, we can see that the \(x\) variables from the specification, the controller and the counter are in conflict.
+To resolve the conflict the conflicted variables are renamed depending on where they come from.
+
+In the state \(R1S\) the composition produces 1 transition out of the \(\tau\) transition.
+The simplified transition is described before, yet examining the composition process can illustrate how value passing work.
+The obtained guard is \(\top \wedge \top \wedge \top \wedge \theta\mpar{x} = \theta\mpar{17} \wedge \act{set}\mpar{x} = \act{set}\mpar{x_R}\) and the obtained variable assignment is \(\mbrc{t \gets x_R, c \gets 0}\).
+We can see how value passing works in the equality constraints: the only possible value of \(x\) and \(x_R\) making the guard hold is \(17\), this value has been synchronised from the controller to \(x\) then to the second occurrence of \(x\) to the distinct \(x\) of the counter.
+Note that \nmm{\OT{S}{C}{\act{set}\mpar{t}}{\mbrc{}}{\top}{\mbrc{c \gets 0}}} wouldn't have worked as a transition for the controller because \(t\) is not a transition variable, its value is fixed before the transition and cannot be set outside of the variable update, hence the use of an auxiliary variable \(x\).
+
+From this point the guard and transition will always be simplified.
 \end{exi}
@@
 Reflexivity, transitivity and preorder are classical properties on relations.
-Completeness w.r.t.\@ composition is the fact that every composition is considered a refinement.
-Correctness w.r.t.\@ composition is the fact that a refinement correspond to the left automaton being equivalent to some composition of the right automaton.
+Correctness w.r.t.\@ composition is the fact that every composition is considered a refinement.
+Completeness w.r.t.\@ composition is the fact that a refinement correspond to the left automaton being equivalent to some composition of the right automaton.
 Context refinement is the refinement being compatible with composition of the same automaton.
@@
 The relations will have to be at least preorders, simulations and forbid the introduction of deadlocks (state where no transition is possible) to be called refinement simulation.
-On top of that weak refinement are refinement where some actions, typically one named \(\tau\), are considered not observable and do not have to be matched.
+On top of that weak refinement are refinement where some actions, typically one named \(\tau\), are considered not observable and can occur in the implementation while not having to be matched in the specification.
 In the weak refinement the relations have to forbid the introduction of livelocks (only a sequence of \(\tau\) possible) and respect \(\tau\)-stuttering \marginpar{cite many things arround here}.
@@
 \end{defi}
-Now let's adapt the properties about states of automata to open automata.
+Now the properties about states of automata can be adapted to open automata.
 \begin{defi}[Simulation on open automata]
@@
 \input{register_anytick.tex}
-\caption{On the left: A clock which imposes a tick; On the right: A modified version of the register at figure \ref{fig:tlh}}
+\caption{On the left: A clock which imposes a tick; On the right: A modified version of the counter at figure \ref{fig:tlh}}
 \label{fig:anytick}
@@
 It is not a coincidence because their goal is to caracterise the same kind of compatibility between automata.
-Actually it is possible to simplify both definition and make them shockingly similar.
+Actually it is possible to simplify both definition and make them even more similar.
 
@@
 This new substitution can replace the standard substitution in the case where only one hole is filled and also in the parallel case.
-In the parallel case the condition is checked after the parallel substitution because there is no guarantee that any order of sequential composition is non-locking for every substitution even if the parallel substitution is non-locking:
-\begin{exi}
-An example of non-locking parallel substitution where no individual substitution is non-locking is given % TODO HERE
+In the parallel case the condition is checked after the parallel substitution because there is no guarantee that any order of sequential composition is non-locking for every substitution even if the parallel substitution is non-locking.
+\begin{exi} % TODO
+\begin{figure}
+\centering
+\input{}
+\vrule
+\input{}
+\vrule
+\input{}
+\caption{}
+\label{fig:pnls}
+\end{figure}
+An example of non-locking parallel substitution where no individual substitution is non-locking is given in Figure \ref{fig:pnls}.% TODO HERE
 \end{exi}
 From this point and in the previous definitions, composition will only refer to non-locking composition.
-
-% ``Composition completeness" can be modified into ``Deadlock reduction completeness" to be compatible with ``Deadlock reduction": \(\forall a\, b, a\mbrk{b} \sqsubseteq a \implies a\mbrk{b} \leq a\).
-% Only the latter will be considered.
-% Similar issues arise on other properties and can be fixed by changing the prerequisites to ensure that the most deadlock-prone composition of automata is composition complete:
-% \begin{description}
-% \item[Composition context equivalence modified:] \(\forall a\, b\, c, a \leq b \wedge a\mbrk{c} \leq a \implies a\mbrk{c} \leq b\mbrk{c}\);
-% \item[Composition congruence modified:] \(\forall a\, b\, c, a \leq b \wedge c\mbrk{a} \leq c \implies c\mbrk{a} \leq c\mbrk{b}\);
-% \item[Composition compatibility modified:] \(\forall a\, b\, c\, d, a \leq b \wedge c \leq d \wedge c\mbrk{a} \leq c \implies c\mbrk{a} \leq d\mbrk{b}\);
-% \end{description}
 

### 2021-05-06 2021-Refinement/report.tex
A few more comments

--- 2021-05-06 2021-Refinement/report.tex
@@
 
-In this article we introduce a refinement relation for open automata\marginpar{TODO: expand}.
+In this article we introduce a refinement relation for open automata. % TODO: expand
 
@@
 Throughout this paper, tuples might be noted differently depending on what they represent.
+Quantification will be used loosely, any bound name in a quantification means that the object is constrained to have that previous value, and any new name is bound by the quantifier.
+For instance \(\forall \mpar{x, y}, \exists \mpar{x', y}, P\) means \(\forall \mpar{x, y}, \exists \mpar{x', y'}, y = y' \wedge P\).
+\Ludo{Strange}{do we really need this interpretation of quantifiers? I find it disturbing}
 
 Family of values, or equivalently maps will be noted \(\mset{i \mapsto x_i}{i \in I}\), \(\mset{i \gets x_i}{i \in I}\) or \(x_i^{i \in I}\).
-The latter will only be used when there is a generating expression; for instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\).
-However \(\mbrc{\alpha \mapsto 1, \beta \mapsto 2, \gamma \mapsto 3}\) has no generating expression and is represented with the first notation in a finite context.
+The latter will only be used when unambiguous; for instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\), but \(\mbrc{\alpha \mapsto 1, \beta \mapsto 2, \gamma \mapsto 3}\) must be represented with one of the two first notation.
+\Ludo{Strange}{ you mean the last notation is forbidden? but isn't it introduced before?}
 The disjoint union of two maps \(\varphi: I \to X\) and \(\psi: J \to Y\) with \(I \cap J = \emptyset\) is \(\varphi \uplus \psi: I \uplus J \to X \cup Y\).
 
-In a formula, a quantifier followed by a finite set will be used as a shorthand for the quantification on every variable in the set:
-\(\forall \mbrc{a_1, \dots, a_n}, \exists \mbrc{b_1, \dots, b_m}, P\) means \(\forall a_1, \dots, \forall a_n, \exists b_1, \dots, \exists b_m, P\).
+For a relation \(\wrel{}{}{}\) which uses a property \(P\) to prove that two element are related \(\forall x \, x', x \wrel{}{}{} x' \iff \exists w: P\mpar{x, x'}\), the fact that there is a valid witness \(w: P\mpar{x, x'}\) is noted \(\wrel{x}{x'}{w}\).
+\Ludo{Strange}{not clear: it seems that $w$ is useless  I guess you mean $P$ depend on $w$ but it is not exactly what is written}
 
@@
 An element \(\mpar{l, t} \in \actions\) is noted \(l\mpar{t}\).
-The formulae contain at least first order logic terms with an equality relation.
-This equality relation is not necessarily a syntactic equality (\(2 + 2 \neq 4\) with a syntactic equality) on \(\terms\).
+The formulae contain at least first order logic terms with an equality relation that is not necessarily \Ludo{?}{restricted to?} the equality on \(\terms\).
 
@@
 
-Values will be used for keeping a variable state, and then injected in terms for substitution.
-This is correct when \(\values \subseteq \rterms\) and we suppose it is the case.
-Otherwise it doesn't invalidates theorem because it can stand as a shorthand for substitution with any term which is interpreted as \(v\).
+\Ludo{?}{I do not understand the meaning of the net paragraph: I must have missed something}
+
+A value \(v\) may be used for keeping a variable state, and then injected in terms for substitution.
+While this is correct when \(\values \subseteq \rterms\), in the other cases this will be used as a shorthand for substitution with any term which can be interpreted as \(v\).
 We suppose that the interpretation of terms is compatible w.r.t.\@ substitution, that is if two terms \(t\), \(t'\) are interpreted with the same value, then replacing \(t\) by \(t'\) in a well-formed expression makes an equivalent well-formed expression.
-\begin{noti}[Notations for separating external logic and logic on \(\formulae\)]
+\begin{noti}
+\defitem In a formula, a quantifier followed by a finite set will be used as a shorthand for the quantification on every variable in the set:
+\[ \forall \mbrc{a_1, \dots, a_n}, \exists \mbrc{b_1, \dots, b_m}, P \text{ means } \forall a_1, \dots, \forall a_n, \exists b_1, \dots, \exists b_m, P \]
+% Also valuations \(\sigma: V \to \values\) will be used as formulas, the interpretation is as expected the constraint of variable to their associated value: \nmm{\bigwedge_{v \in V} v = \sigma\mpar{v}}.
 \defitem The satisfiability relation will be noted using the classical relational notation \(\vdash f\).
@@
 \begin{defi}[Open automaton]
-A open automaton is a tuple \(\OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(S\) the set of states, \(s_0 \in S\) the initial state, \(V\) the set of variable names unique to this automaton, \(\sigma_0: V' \to \values\) the initial valuation of variables where \(V' \subseteq V\), \(J\) the set of hole names and \(T\) the set of open transitions.
+A open automaton is a tuple \(\OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(S\) the set of states, \(s_0 \in S\) the initial state, \(V\) the set of variable names unique to this automaton, \(\sigma_0: V' \to \values\) the initial valuation of variables where \(V' \subseteq V\), \(J\) the set of hole names and \(T\) a set of open-transitions.
 
@@
 The variable names may clash when considering two automata, in that case we suppose that we can still distinguish the variables in the formulas.
-% The open transitions will be considered to be a finite set of representative open transitions. Removing this restriction may break some theorems.
+All the possible open transitions, from which transitions in \(T\) are selected, are defined below.
 The initial valuation may be a partial valuation of the variables, if the undefined variables are set before being read this behave like a normal variable.
@@
 \end{defi}
-An open transition can have many unbound variable, actually an effective transition of the automaton is any well-formed substitution of the unbound variables of the transition minus the automaton variables.
-This is used to constrain the infinite branching to be representable, making it possible to reason about.
+An open transition can have many unbound variable, actually any well-formed substitution of the unbound variables of the transition minus the automaton variables is a transition that the open automaton can perform.
 
@@
 This automaton is an implementation of the enable operator because it begins in the state \(L\) where it allows any transition from its hole \(l\) which is not \(\delta\) then the automaton synchronises its holes on the same data, effectively allowing a data exchange when it goes into state \(R\), and finally allows any transition from its hole \(r\).
-We use the standard convention that uses \(\tau\) as a non-observable transition, never synchronised with other actions and passed unmodified.
-This allows the synchronisation of the two holes to be hidden to the exterior by sending a \(\tau\).
-However here \(\tau\) is not always allowed from the holes, for instance in the state \(L\) the hole \(r\) cannot emit it.
-These transition have been omitted for the sake of simplifying the first example of open automaton.
+We use the standard convention that uses $\tau$ as a non-observable transition, never synchronised with other actions and passed unmodified.
+Here the synchronisation is hidden to the exterior by sending a \(\tau\).
+\Ludo{Well}{avoid informal English in scientific writing} here \(\tau\) is not always allowed from the holes in the state \(L\) the hole \(r\) cannot emit it for the sake of simplifying the first example of open automaton.
+\end{exi}
+\begin{exi}[Enable, variable-oriented]
+The automata drawn on the right side of the figure is an alternative implementation of the enable operator which is FH-bisimilar to the previous one\footnote{FH-bisimulation is defined in ~\cite{addcitation}}.
+The drawing introduces the double arrows which is used to denote the initial valuation.
+The automata drawn is \(\OA{\mbrc{\_}}{\_}{\mbrc{v}}{l^\mbrc{v}}{\mbrc{l, r}}{T}\) where transitions in \(T\) are like previously all the transitions generated by
+\begin{align*}
+	\OT{\_}{\_}{x}{\mbrc{l \mapsto x}}{v = l \wedge x \neq \delta}{\mbrc{}} &&
+	\OT{\_}{\_}{\tau}{\mbrc{l \mapsto \delta\mpar{x}, r \mapsto \act{acc}\mpar{y}}}{v = l \wedge x = y}{\mbrc{v \gets r}} &&
+	\OT{\_}{\_}{x}{\mbrc{r \mapsto x}}{v = r}{\mbrc{}}
+\end{align*}
+Note that in this example \(r\) is a hole name and also a closed term, but not a variable.
+The same applies for \(l\).
+\(v\) is a variable name for the automaton and a variable in the guard, \Ludo{so its value is not substituted}{I do not understand this: it seems to mean that the substitution of v has no effect}.\Ludo{?}{I believe this needs to be explained more clearly, perhaps based on the def 6 below}
+For instance \nmm{\OT{\_}{\_}{\tau}{\mbrc{l \mapsto \tau}}{v = l \wedge \tau \neq \delta}{\mbrc{}}} is in \(T\) but not \nmm{\OT{\_}{\_}{\tau}{\mbrc{l \mapsto \tau}}{l = l \wedge \tau \neq \delta}{\mbrc{}}} (result of the substitution \(v \mapsto l\)).
+
+An imaginary run of this open automaton can be the automaton in the hole \(l\) emits many actions, this synchronises with the only transition possible at that moment because \(v = l\).
+Then the automaton in hole \(l\) emits a \(\delta\mpar{t}\), this is synchonised with the action that sets \(v \gets r\) and the automata in hole \(r\) must emit a \(\act{acc}\mpar{t}\).
+Finally the automaton in the hole \(r\) emits any sequence of action.
+
+Another imaginary run can be the automaton in the hole \(l\) emits a sequence of action and the automaton in the hole \(r\) cannot emit a \(\act{acc}\mpar{t}\) so it never runs.
 \end{exi}
@@
 	\fguard{\OTg} & \defnotation g &
-	\fOT{t} & \defnotation \mset{\OTg \in T}{s = t} &
-	\fIT{t} & \defnotation \mset{\OTg \in T}{s' = t}
+	\fOT{s} & \defnotation \mbrc{\OTg \in T}
 \end{align*}
@@
 \end{defi}
-
-\begin{exi}[Enable, variable-oriented]
-The automata drawn on the right side of the figure is an alternative implementation of the enable operator which is FH-bisimilar to the previous one.
-The drawing introduces the double arrows which is used to denote the initial valuation.
-The automata drawn is \(\OA{\mbrc{\_}}{\_}{\mbrc{v}}{l^\mbrc{v}}{\mbrc{l, r}}{T}\) where transitions in \(T\) are like previously all the transitions generated by
-\begin{align*}
-	\OT{\_}{\_}{x}{\mbrc{l \mapsto x}}{v = l \wedge x \neq \delta}{\mbrc{}} &&
-	\OT{\_}{\_}{\tau}{\mbrc{l \mapsto \delta\mpar{x}, r \mapsto \act{acc}\mpar{y}}}{v = l \wedge x = y}{\mbrc{v \gets r}} &&
-	\OT{\_}{\_}{x}{\mbrc{r \mapsto x}}{v = r}{\mbrc{}}
-\end{align*}
-Note that in this example \(r\) and \(l\) are a hole names and also closed terms: this is a naming conflict, we do not have \(J \subseteq \rterms\).
-
-The variables of a transition are all the free variables in the expressions minus the auomaton variables.
-For instance \(v\) is a variable name for the automaton which is used in the guard.
-It is not a transituon variable.
-When generating transition without free variables its value is not substituted with a closed term.
-For instance \nmm{\OT{\_}{\_}{\tau}{\mbrc{l \mapsto \tau}}{v = l \wedge \tau \neq \delta}{\mbrc{}}} is a transition generated by the second transition and is in \(T\) but not \nmm{\OT{\_}{\_}{\tau}{\mbrc{l \mapsto \tau}}{l = l \wedge \tau \neq \delta}{\mbrc{}}} (result of the forbidden substitution \(v \mapsto l\)).
-
-An imaginary run of this open automaton can be the automaton in the hole \(l\) emits many actions, this synchronises with the only transition possible at that moment because \(v = l\).
-Then the automaton in hole \(l\) emits a \(\delta\mpar{t}\), this is synchonised with the action that sets \(v \gets r\) and the automata in hole \(r\) must emit a \(\act{acc}\mpar{t}\).
-Finally the automaton in the hole \(r\) emits any sequence of action.
-
-Another imaginary run can be the automaton in the hole \(l\) emits a sequence of action and the automaton in the hole \(r\) cannot emit a \(\act{acc}\mpar{t}\) so it never runs.
-\end{exi}
-
 From this point open automata and open transitions will be called automata and transitions for simplicity.
@@
 
-Figure \ref{fig:tls} shows the light controller with some synchronisation logic.
+\Ludo{Figure \ref{fig:tls} shows}{rephrased: typo} the light controller with some synchronisation logic.
 It  takes an unimplemented control circuit in the hole \(C\) which gives the timings and an also unimplemented register in the hole \(R\) to count external \(\act{tick}\) actions.
@@
 \end{figure}
-The component we choose to compose in the holes are in Figure \ref{fig:tlh}.
+The component we choose to compose in the holes are in \Ludo{F}{}igure \ref{fig:tlh}.
 On the left is the controller agent which will be composed in the hole \(C\).
@@
 \defitem \textbf{a preorder} iff it is reflexive and transitive;
-\defitem \textbf{correct w.r.t.\@ composition} iff \(\forall a\, b, a\mbrk{b} \leq a\);
-\defitem \textbf{complete w.r.t.\@ composition} iff \(\forall a\, b, a \leq b \implies \exists c, a \overset{FH}= b\mbrk{c}\);
-\defitem \textbf{context refining for composition} iff \(\forall a\, b\, c, a \leq b \implies a\mbrk{c} \leq b\mbrk{c}\);
+\defitem \textbf{\Ludo{complete}{not sure whyy this is called completeness} w.r.t.\@ composition} iff \(\forall a\, b, a\mbrk{b} \leq a\);
+\defitem \textbf{\Ludo{correct}{This eems very difficult to achieve so calling it correctness and implying that the other relations are not interesting is very strong} w.r.t.\@ composition} iff \(\forall a\, b, a \leq b \implies \exists c, a \overset{FH}= b\mbrk{c}\);
+\defitem \textbf{context \Ludo{equivalent}{equivalent is strange here as there is no equivalence as far as I can see} for composition} iff \(\forall a\, b\, c, a \leq b \implies a\mbrk{c} \leq b\mbrk{c}\);
 \defitem \textbf{congruent for composition} iff \(\forall a\, b\, c, a \leq b \implies c\mbrk{a} \leq c\mbrk{b}\);
@@
 Correctness w.r.t.\@ composition is the fact that a refinement correspond to the left automaton being equivalent to some composition of the right automaton.
-Context refinement is the refinement being compatible with composition of the same automaton.
+Context equivalence is the refinement being compatible with composition with the same automaton.
 Congruence is the refinement being compatible with being composed in the same automaton.
-Compatibility with composition is the conjunction of the two latter (assuming the relation is a preorder).
+Compatibility with composition is the two latter at the same time \Ludo{?}{(plus transitivity?) it depends what you mean by ``at the same time''}.
 Finally compatibility with FH-bisimulation is the refinement not being able to distinguish two FH-bisimilar automata.
 
-The relations will have to be at least preorders, simulations and forbid the introduction of deadlocks (state where no transition is possible) to be called refinement simulation.
-On top of that weak refinement are refinement where some actions, typically one named \(\tau\), are considered not observable and do not have to be matched.
-In the weak refinement the relations have to forbid the introduction of livelocks (only a sequence of \(\tau\) possible) and respect \(\tau\)-stuttering \marginpar{cite many things arround here}.
+The relations will have to be at least preorders, simulations and forbid the \Ludo{introduction of deadlocks}{define more precisely introduction of deadlocks or refer to a future definition} (states where no transition is possible) to be called refinement simulation.
+On top of that weak refinements are refinement where some actions, typically one named \(\tau\), are considered not observable and do not have to be matched.
+In  weak refinements, the relations have to forbid the introduction of livelocks (only a sequence of \(\tau\) possible) and respect \(\tau\)-stuttering \marginpar{cite many things arround here}.\Ludo{to add}{I believe we want more arguments on why we want some properties, at least deadlock and livelock related, perhaps also weak vs strong.
+How did you decide of the list of useful properties / when ais such or such property useful?}
 While being preorder is simple to express for a relation, being a simulation, do not introduce new deadlocks/livelocks and \(\tau\)-stuttering are properties about the states of the related automata, therefore they are more complex to express.
@@
 
-Two states \(s_1 \in S_1, s_2 \in S_2\) are related under a valuation \(\sigma: V_1 \uplus V_2 \to \values\) iff \(\sigma \vdash R\mpar{s_1, s_2}\).
-For a relation \(\wrel{}{}{}\) which uses a relation under predicate to prove that two element are related \(\forall x \, x', x \wrel{}{}{} x' \iff \exists R, P\mpar{R}\), the fact that there is a valid witness \(R\) is noted \(\wrel{x}{x'}{R}\).
+Two states \(s_1 \in S_1, s_2 \in S_2\) are related under a \Ludo{?}{relation is mission: under a relation $R$ for a valuation ...
+?} valuation  \(\sigma: V_1 \uplus V_2 \to \values\) iff \(\sigma \vdash R\mpar{s_1, s_2}\).
 \end{defi}
-Now let's adapt the properties about states of automata to open automata.
+Now, we adapt the properties about states of automata to open automata.
 \begin{defi}[Simulation on open automata]
-A relation \(\leq\) is a simulation if for any related automata \(\wrel{A_1}{A_2}{R}\) where \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\), \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and \(R: S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\), \(R\) satisfies both
+A relation \(\leq\) is a simulation if for any two related automata \(\wrel{A_1}{A_2}{R}\) where \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\), \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and \(R: S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\), \(R\) satisfies both
 \defitem Initial states are related under initial valuations: \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\);
-\defitem From related states, all out-transitions from \(A_1\) can be simulated in \(A_2\) and their target states are related:
+\defitem From related states, all out-transitions from \(A_1\) can be simulated in \(A_2\) and their target states are \Ludo{related}{I am a bit surprised that $J_1$ and $J_2$ are unrelated and we only need to take only the intersection TBD}:
 \begin{multline*}
-	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \forall \sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values, \\
-	\mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \\
+	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in T_1, \forall \sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values, \\
+	\mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} t_2 \defobject \OTx{2}{}{2}{2} \in T_2, \exists \nu: \fvars{t_2} \to \values, \\
 	\sigma \uplus \nu \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
@@
 The last formula means that for every pair of related states under valuation of the automaton variables and every possible transitions (\(\vdash g_1\)) from the first automaton, there is a possible transition (\(\vdash g_2\)) such that the produced action matches (\(\alpha_1 = \alpha_2\)), the holes actions from same hole names (\(J'_1 \cap J'_2\)) match (\(\beta_{1j} = \beta_{2j}\)) and the target states are related after variable update.
-This is a natural extenion of the notion of simulation on LTS, which is the same definition without variables and holes and guards.
+This is a natural extension of the notion of simulation on LTS, which is the same definition without variables and holes and guards.
 It will serve as a watchdog for any relation that will be defined with ``simulation" in its name, except weak-simulation where the transition from the first automaton that produce \(\tau\) actions are excluded.
@@
 	\mpar{\everymath{\displaystyle}\begin{array}{c}
-		\bigsymb{\exists} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_1} \uplus \fvars{t_2} \to \values, \\
+		\bigsymb{\exists} t_1 \defobject \OTx{1}{}{1}{1} \in T_1, t_2 \defobject \OTx{2}{}{2}{2} \in T_2, \exists \nu: \fvars{t_1} \uplus \fvars{t_2} \to \values, \\
 		\sigma \uplus \nu \vdash g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
@@
 \end{defi}
-This definition extends the requirements of a simulation by requiring from the relation that on related states, either there is a pair of possible matching transition or there was no out-transition possible in the specification.
+This definition \Ludo{extends the requirements of a simulation}{je suis pas d accord avec cette affirmation, ou tout du moins c est pas evident} by requiring from the relation that on related states, either there is a pair of possible matching transition or there was no out-transition possible in the specification.
 This requirement effectively prevents the presence of deadlock state in the first automaton if there is a related non-deadlock state in the second.
@@
 ``Deadlock reduction" conflicts with ``composition completeness" by disallowing some unwanted cases where an automaton in a hole cannot produce any action that any out-transitions expects.
-In particular filling a hole with the deadlock automaton (only one state without out-transitions) is not considered a refinement for a no deadlock reducing simulation refinement.
-A way to solve this issue is to caracterise a composition that do not introduce deadlocks, which will be used instead of the composition introduced earlier.
+In particular filling a hole with the deadlock automaton (only one state without out-transitions) is not considered a refinement for a \Ludo{no deadlock reducing simulation refinement}{define or use the name of the definition}.
+A way to solve this \Ludo{issue}{why is this an issue?
+can be solved by stating which properties are desirable for which reason above} is to characterise a composition that do not introduce deadlocks, which will be used instead of the composition introduced earlier.
 \begin{defi}[Reachability]
-For any open automata \(A \defobject \OA{S}{s_0}{V}{\sigma_0}{J}{T}\), a reachability predicate \(\reach{A}: S \to \rformulae[V]\) is a predicate on states such that
+For any open automata \(A \defobject \OA{S}{s_0}{V}{\sigma_0}{J}{T}\), we define the caracterisation of reachable valuations \(\reach{A}: S \to \rformulae[V]\) as the strongest predicate on states such that
 \defitem \(\sigma_0 \vdash \reach{A}\mpar{s_0}\).
@@
 \end{defi}
-For the reader not used to simulations and bisimulations, this definition of a predicate can seem strange.
+For the reader not used to simulations and bisimulations, this definition with \Ludo{a witness}{what is the witness in the definition above?} can seem strange.
 The reachability predicate is used to caracterise the states and valuations that are reachable in a run of an automaton.
-In fact the role of the predicate is to caracterise potentially reachable configurations without having to caracterise the fact that the state and valuation are the result of a valid path in an automaton.
+In fact the role of the witness is to caracterise reachable configurations without having to caracterise the fact that the state and valuation are the result of a valid path in an automaton.
 
 To do that we impose that the initial state is reachable in the initial valuation and that reachability is preserved by taking valid transitions.
-This effectively makes reachability account for all paths and potentially over-approximate the reachable configurations.
-However the exact rechability may not be reprensentable in the formulae, hence the need of potentially over-approximating.
-
-Another way of understanding this predicate is that it is a fixpoint of the union of valuations that contains the initial valuation:
+This effectively makes reachability account for all paths, and to not account for impossible path the strongest predicate is used.
+Another way of understanding this predicate is that it is the least fixpoint of the union of valuations that contains the initial valuation:
 \begin{align*}
-	f\mpar{p} = s' \mapsto p\mpar{s'} \vee \bigsymb{\bigvee_\subbox{\OTg \,\in\, \fIT{s'}}} p\mpar{s}\psubst{\psi} \wedge g &&
-	\sigma_0 \vdash \reach{A}\mpar{s_0} &&
-	f\mpar{\reach{A}} = \reach{A}
+	f\mpar{p} = s' \mapsto p\mpar{s'} \vee \bigsymb{\bigvee_\subbox{\OTg \,\in\, T}} p\mpar{s}\psubst{\psi} \wedge g &&
+	\reach{A} = \lim_n f^n\mpar{s \mapsto \choice{\sigma_0 & s = s_0 \\ \bot & \text{otherwise}}}
 \end{align*}
@@
 \begin{defi}[Non-locking composition, intuitive definition]
-The composition resulting in \(A_p\subst{A_c}{k} = \OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(A_c \defobject \OA{S_c}{s_{0c}}{V_c}{\sigma_{0c}}{J_c}{T_c}\), \(A_p \defobject \OA{S_p}{s_{0p}}{V_p}{\sigma_{0p}}{J_p}{T_p}\) and \(k \in J_p\), is a non-locking composition if there is a rechability predicate such that from reachable configurations, either a transition is possible in \(A_p\subst{A_c}{k}\) or there were no possible transition in \(A_p\) to begin with
+The composition  \(A_p\subst{A_c}{k} = \OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(A_c \defobject \OA{S_c}{s_{0c}}{V_c}{\sigma_{0c}}{J_c}{T_c}\), \(A_p \defobject \OA{S_p}{s_{0p}}{V_p}{\sigma_{0p}}{J_p}{T_p}\) and \(k \in J_p\), is a non-locking composition if:
+\defitem From reachable configurations, either a transition is possible in \(A_p\subst{A_c}{k}\) or there were no possible transition in \(A_p\) to begin with
 \begin{multline*}
-	\forall s \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A_p\subst{A_c}{k}}\mpar{s}} \implies \mpar{\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t}} \\
+	\forall s \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A_p\subst{A_c}{k}}\mpar{s}} \implies \mpar{\exists t \in T, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t}} \\
 	\vee \forall t_p \in \fOT{\pi_{S_p}\mpar{s}}, \forall \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \nvdash \fguard{t_p}
@@
 
-To illustrate the introduction of a deadlock in a composition and the definition of non-locking composition, let's look at an example.
+To illustrate the introduction of a deadlock in a composition and the definition of non-locking composition, we consider the following example.
 \begin{exi}[Deadlocks introduced by composition]
-% TODO: give a context, a circuit cannot block physical time from progressing
+% TODO HERE: read CCSL & BIP
 \begin{figure}
@@
 
-This new substitution can replace the standard substitution in the case where only one hole is filled and also in the parallel case.
-In the parallel case the condition is checked after the parallel substitution because there is no guarantee that any order of sequential composition is non-locking for every substitution even if the parallel substitution is non-locking:
-\begin{exi}
-An example of non-locking parallel substitution where no individual substitution is non-locking is given % TODO HERE
-\end{exi}
+This new substitution can replace the standard substitution in the case where only one hole is filled and also in the parallel case:
+\begin{thm}[Parallel non-locking substitution]
+Let \(A, B, C\) be open automata, \(J_A\) the hole names of \(A\) and \(k, l \in J_A\) two distinct hole names.
+\[ A\subst{B}{k}\subst{C}{l} \iff A\subst{C}{l}\subst{B}{k} \]
+\end{thm}
+If we prove that, then they are bisimilar because non-locking composition is a restriction of standard composition.
+\begin{proof}
+Both ways are symmetric so we will only prove one way.
+Let \(s' \defobject \mpar{\mpar{s_A, s_C}, s_B}\) and \(\sigma: V_A \uplus V_C \uplus V_B \to \values\) be respectively a state and a valuation of \(A\subst{C}{l}\subst{B}{k}\).
+We need to prove both:
+\begin{gather}
+	\sigma \vdash \reach{A\subst{C}{l}} \wedge \bigvee_\subbox{t \in \fOT{s_A}} \fguard{t} \implies \bigvee_\subbox{t \in \fOT{s_A, s_C}} \fguard{t} \goal{1} \\
+	\sigma \vdash \reach{A\subst{C}{l}\subst{B}{k}} \wedge \bigvee_\subbox{t \in \fOT{s_A, s_C}} \fguard{t} \implies \bigvee_\subbox{t \in \fOT{s'}} \fguard{t} \goal{2}
+\end{gather}
+\(\mpar{s_A, s_B}\) is a state of \(A\subst{B}{k}\), \(s \defobject \mpar{\mpar{s_A, s_B}, s_C}\) is a state of \(A\subst{B}{k}\subst{C}{l}\) and \(\sigma\) is a valuation of their variables so the following hold by hyptoheses:
+\begin{gather}
+	\sigma \vdash \reach{A\subst{B}{k}} \wedge \bigvee_\subbox{t \in \fOT{s_A}} \fguard{t} \implies \bigvee_\subbox{t \in \fOT{s_A, s_B}} \fguard{t} \hyp{1} \\
+	\sigma \vdash \reach{A\subst{B}{k}\subst{C}{l}} \wedge \bigvee_\subbox{t \in \fOT{s_A, s_B}} \fguard{t} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{2}
+\end{gather}
+By admitting and decomposing the left part of \goal{1} and \goal{2} we get the following:
+\begin{align*}
+	\sigma \vdash \reach{A\subst{C}{l}} & \text{ \hyp{\_}} &
+	t_A \in \fOT{s_A} &&
+	\sigma \vdash \fguard{t_A} \text{ \hyp{2}} \\
+	\sigma \vdash \reach{A\subst{C}{l}\subst{B}{k}} & \text{ \hyp{3}} &
+	t_{AC} \in \fOT{s_A, s_C} &&
+	\sigma \vdash \fguard{t_{AC}} \text{ \hyp{4}}
+\end{align*}
+And now we need to prove:
+\begin{align*}
+	\sigma \vdash \bigvee_\subbox{t \in \fOT{s_A, s_C}} \fguard{t} & \text{ \goal{1'}} &
+	\sigma \vdash \bigvee_\subbox{t \in \fOT{s'}} \fguard{t} & \text{ \goal{2'}}
+\end{align*}
+We use the fact that \(A\subst{C}{l}\subst{B}{k} \cong A\subst{B}{k}\subst{C}{l}\) on \hyp{3} to get: % TODO HERE: Add lemma about reachability implication for composition
+\[ \sigma \vdash \reach{A\subst{B}{k}\subst{C}{l}} \hyp{5} \]
+% TODO
+\end{proof}
 From this point and in the previous definitions, composition will only refer to non-locking composition.
@@
 \begin{defi}[Hole-identical simulation]
-\Quentin{``\(R\) is a hole-identical simulation of \(A_1\) in \(A_2\)"}{Any idea on how to note that? \(R \vDash A_1 \leq_= A_2\) for instance.} is defined as: % TODO: \wrel
+\Quentin{``\(R\) is a hole-identical simulation of \(A_1\) in \(A_2\)"}{Any idea on how to note that?
+\(R \vDash A_1 \leq_= A_2\) for instance.} is defined as: % TODO: faire des macros, + A_1 \overset{=}\leq_R A_2
 \begin{multline*}
@@
 	\mpar{\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{} \in \fOT{s_2}}^{x \in X}, \\[12pt]
+		\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{} \in T_2}^{x \in X}, \\[12pt]
 		\forall \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\
@@
 \mpar{\everymath{\displaystyle}\begin{array}{l}
-	\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{} \in \fOT{s_2}}^{x \in X}, \\[12pt]
+	\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{} \in T_2}^{x \in X}, \\[12pt]
 	\forall \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\
@@
 \mpar{\everymath{\displaystyle}\begin{array}{l}
-	\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\[6pt]
-	\quad \mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} \OTx{2}{}{2}{2} \in \fOT{s_2}, \\[12pt]
+	\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in T_1, \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\[6pt]
+	\quad \mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} \OTx{2}{}{2}{2} \in T_2, \\[12pt]
 	\qquad \sigma \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
@@
 \begin{proof} Let \(\mpar{s_1, s_2} \in S_1 \times S_2\),
-\item[\(\implies\):] We admit the up formula as \(H_{def}\), let \(t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}\) and \(\sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values\) be such that \(H_{source} \defobject \sigma \vdash R\mpar{s_1, s_2} \wedge g_1\).
-	\(H_{def}\) applied to \(t_1\) gives \(\mpar{t_{2x} \defobject \OTx{2}{x}{2x}{1} \in \fOT{s_2}}^{x \in X}\) and the property \(H_{tmp}\) to which we give \(\sigma\) to get
+\item[\(\implies\):] We admit the up formula as \(H_{def}\), let \(t_1 \defobject \OTx{1}{}{1}{1} \in T_1\) and \(\sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values\) be such that \(H_{source} \defobject \sigma \vdash R\mpar{s_1, s_2} \wedge g_1\).
+	\(H_{def}\) applied to \(t_1\) gives \(\mpar{t_{2x} \defobject \OTx{2}{x}{2x}{1} \in T_2}^{x \in X}\) and the property \(H_{tmp}\) to which we give \(\sigma\) to get
 	\begin{multline*}
@@
 	\mpar{\renewcommand\arraystretch{1.4}\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
+		\bigsymb{\forall} \OTx{1}{}{1}{1} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in T_2}^{x \in X}, \\
 		\mpar{\forall x \in X, J'_1 = J'_{2x} \cap J_1} \wedge \forall \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\
@@
 	\mpar{\renewcommand\arraystretch{1.4}\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
+		\bigsymb{\forall} \OTx{1}{}{1}{1} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in T_2}^{x \in X}, \\
 		\mpar{\forall x \in X, J'_1 \cap J_2 = J'_{2x} \cap J_1 \wedge f\mpar{J'_1 \setminus J_2} \subseteq J'_{2x}} \wedge \forall \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\
@@
 	\mpar{\renewcommand\arraystretch{1.4}\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_1}}^{x \in X}, \\
+		\bigsymb{\forall} \OTx{1}{}{1}{1} \in T_1, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in T_1}^{x \in X}, \\
 		\mpar{\forall x \in X, J'_1 \cap J_2 = J'_{2x} \cap J_1 \wedge f\mpar{J'_1 \setminus J_2} \subseteq J'_{2x}} \wedge \forall \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\

### 2021-05-06 2021-Refinement/Traffic_Lights_Spec.tex
Introducing some examples, removing pdf, correcting some line ends
Composisiton example fully integrated

@@
 
-\node[state,initial] (v1) at (150:4) {R};
-\node[state] (v2) at (30:4) {G};
-\node[state] (v3) at (270:4) {Y};
+\node[state,initial] (v1) at (150:3.5) {R};
+\node[state] (v2) at (30:3.5) {G};
+\node[state] (v3) at (270:2) {Y};
 
-\draw (v1) edge[dir=220] node[below] {\OTd{\act{tick}}{R \mapsto \act{tick}}{}} (v1);
+\draw (v1) edge[dir=220] node[below] {\OTd{\act{tick}}{cnt \mapsto \act{tick}}{}} (v1);
 \draw (v1) edge[dir=150] node[left] {\OTd{\act{onRed}}{}{}} (v1);
-\draw (v1) edge[dir=80] node[above] {\OTd{\tau}{C \mapsto \theta\mpar{x}, R \mapsto \act{set}\mpar{x}}{}} (v1);
-\draw (v1) edge node {\OTd{\act{TurnGreen}}{R \mapsto \act{over}\mpar{x}, C \mapsto \delta\mpar{x}}{}} (v2);
-\draw (v2) edge[dir=100] node {\OTd{\act{tick}}{R \mapsto \act{tick}}{}} (v2);
-\draw (v2) edge[dir=30] node {\OTd{\act{onGreen}}{}{}} (v2);
-\draw (v2) edge[dir=320] node {\OTd{\tau}{C \mapsto \theta\mpar{x}, R \mapsto \act{set}\mpar{x}}{}} (v2);
-\draw (v2) edge node {\OTd{\act{TurnYellow}}{R \mapsto \act{over}\mpar{x}, C \mapsto \delta\mpar{x}}{}} (v3);
-\draw (v3) edge[dir=340] node {\OTd{\act{tick}}{R \mapsto \act{tick}}{}} (v3);
+\draw (v1) edge[dir=80] node[above] {\OTd{\tau}{ctl \mapsto \theta\mpar{x}, cnt \mapsto \act{set}\mpar{x}}{}} (v1);
+\draw (v1) edge node {\OTd{\act{TurnGreen}}{cnt \mapsto \act{over}\mpar{x}, ctl \mapsto \delta\mpar{x}}{}} (v2);
+\draw (v2) edge[dir=100] node[above] {\OTd{\act{tick}}{cnt \mapsto \act{tick}}{}} (v2);
+\draw (v2) edge[dir=30] node[right] {\OTd{\act{onGreen}}{}{}} (v2);
+\draw (v2) edge[dir=320] node[xshift=1cm,below] {\OTd{\tau}{ctl \mapsto \theta\mpar{x}, cnt \mapsto \act{set}\mpar{x}}{}} (v2);
+\draw (v2) edge node[pos=0.6] {\OTd{\act{TurnYellow}}{cnt \mapsto \act{over}\mpar{x}, ctl \mapsto \delta\mpar{x}}{}} (v3);
+\draw (v3) edge[dir=340] node {\OTd{\act{tick}}{cnt \mapsto \act{tick}}{}} (v3);
 \draw (v3) edge[dir=270] node {\OTd{\act{onYellow}}{}{}} (v3);
-\draw (v3) edge[dir=200] node {\OTd{\tau}{C \mapsto \theta\mpar{x}, R \mapsto \act{set}\mpar{x}}{}} (v3);
-\draw (v3) edge node {\OTd{\act{TurnRed}}{R \mapsto \act{over}\mpar{x}, C \mapsto \delta\mpar{x}}{}} (v1);
+\draw (v3) edge[dir=200] node {\OTd{\tau}{ctl \mapsto \theta\mpar{x}, cnt \mapsto \act{set}\mpar{x}}{}} (v3);
+\draw (v3) edge node[pos=0.4] {\OTd{\act{TurnRed}}{cnt \mapsto \act{over}\mpar{x}, ctl \mapsto \delta\mpar{x}}{}} (v1);
 

### 2021-05-06 2021-Refinement/report.tex

--- 2021-05-06 2021-Refinement/report.tex
@@
 
-The relations will have to be at least preorders, simulations and forbid the introduction of deadlocks (state where no transition is possible) to be called refinement simulation.
+The relations will have to be at least preorders, simulations and \Ludo{introduction of deadlocks}{define more precisely introduction of deadlocks or refer to a future definition} (state where no transition is possible) to be called refinement simulation.
 On top of that weak refinement are refinement where some actions, typically one named \(\tau\), are considered not observable and can occur in the implementation while not having to be matched in the specification.
 In the weak refinement the relations have to forbid the introduction of livelocks (only a sequence of \(\tau\) possible) and respect \(\tau\)-stuttering \marginpar{cite many things arround here}.
+\Ludo{to add}{I believe we want more arguments on why we want some properties, at least deadlock and livelock related, perhaps also weak vs strong.
+How did you decide of the list of useful properties / when ais such or such property useful?}
+
 While being preorder is simple to express for a relation, being a simulation, do not introduce new deadlocks/livelocks and \(\tau\)-stuttering are properties about the states of the related automata, therefore they are more complex to express.
@@
 
-Two states \(s_1 \in S_1, s_2 \in S_2\) are related under a valuation \(\sigma: V_1 \uplus V_2 \to \values\) iff \(\sigma \vdash R\mpar{s_1, s_2}\).
+Two states \(s_1 \in S_1, s_2 \in S_2\) are related under a \Ludo{?}{relation is mission: under a relation $R$ for a valuation ...
+?} valuation \(\sigma: V_1 \uplus V_2 \to \values\) iff \(\sigma \vdash R\mpar{s_1, s_2}\).
 For a relation \(\wrel{}{}{}\) which uses a relation under predicate to prove that two element are related \(\forall x \, x', x \wrel{}{}{} x' \iff \exists R, P\mpar{R}\), the fact that there is a valid witness \(R\) is noted \(\wrel{x}{x'}{R}\).
@@
 \begin{defi}[Simulation on open automata]
-A relation \(\leq\) is a simulation if for any related automata \(\wrel{A_1}{A_2}{R}\) where \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\), \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and \(R: S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\), \(R\) satisfies both
+A relation \(\leq\) is a simulation if for any two related automata \(\wrel{A_1}{A_2}{R}\) where \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\), \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and \(R: S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\), \(R\) satisfies both
 \defitem Initial states are related under initial valuations: \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\);
-\defitem From related states, all out-transitions from \(A_1\) can be simulated in \(A_2\) and their target states are related:
+\defitem From related states, all out-transitions from \(A_1\) can be simulated in \(A_2\) and their target states are \Ludo{related}{I am a bit surprised that $J_1$ and $J_2$ are unrelated and we only need to take only the intersection TBD}:
 \begin{multline*}
@@
 ``Deadlock reduction" conflicts with ``composition completeness" by disallowing some unwanted cases where an automaton in a hole cannot produce any action that any out-transitions expects.
-In particular filling a hole with the deadlock automaton (only one state without out-transitions) is not considered a refinement for a no deadlock reducing simulation refinement.
-A way to solve this issue is to caracterise a composition that do not introduce deadlocks, which will be used instead of the composition introduced earlier.
+In particular filling a hole with the deadlock automaton (only one state without out-transitions) is not considered a refinement for a \Ludo{no deadlock reducing simulation refinement}{define or use the name of the definition}.
+A way to solve this \Ludo{issue}{why is this an issue?
+can be solved by stating which properties are desirable for which reason above} is to characterise a composition that do not introduce deadlocks, which will be used instead of the composition introduced earlier.
 \begin{defi}[Reachability]
@@
 \end{defi}
+
 For the reader not used to simulations and bisimulations, this definition of a predicate can seem strange.
-The reachability predicate is used to caracterise the states and valuations that are reachable in a run of an automaton.
-In fact the role of the predicate is to caracterise potentially reachable configurations without having to caracterise the fact that the state and valuation are the result of a valid path in an automaton.
+The reachability predicate is used to characterise the states and valuations that are reachable in a run of an automaton.
+In fact the role of the predicate is to characterise potentially reachable configurations without having to characterise the fact that the state and valuation are the result of a valid path in an automaton.
 
@@
 This effectively makes reachability account for all paths and potentially over-approximate the reachable configurations.
-However the exact rechability may not be reprensentable in the formulae, hence the need of potentially over-approximating.
+However the exact reachability may not be reprensentable in the formulae, hence the need of potentially over-approximating.
 
@@
 \begin{defi}[Non-locking composition, intuitive definition]
-The composition resulting in \(A_p\subst{A_c}{k} = \OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(A_c \defobject \OA{S_c}{s_{0c}}{V_c}{\sigma_{0c}}{J_c}{T_c}\), \(A_p \defobject \OA{S_p}{s_{0p}}{V_p}{\sigma_{0p}}{J_p}{T_p}\) and \(k \in J_p\), is a non-locking composition if there is a rechability predicate such that from reachable configurations, either a transition is possible in \(A_p\subst{A_c}{k}\) or there were no possible transition in \(A_p\) to begin with
+
+The composition  \(A_p\subst{A_c}{k} = \OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(A_c \defobject \OA{S_c}{s_{0c}}{V_c}{\sigma_{0c}}{J_c}{T_c}\), \(A_p \defobject \OA{S_p}{s_{0p}}{V_p}{\sigma_{0p}}{J_p}{T_p}\) and \(k \in J_p\), is a non-locking composition if there is a reachability predicate such that from reachable configurations, either a transition is possible in \(A_p\subst{A_c}{k}\) or there were no possible transition in \(A_p\) to begin with
 \begin{multline*}
@@
 
-To illustrate the introduction of a deadlock in a composition and the definition of non-locking composition, let's look at an example.
+To illustrate the introduction of a deadlock in a composition and the definition of non-locking composition, we consider the following example.
 \begin{exi}[Deadlocks introduced by composition]

### 2021-05-06 2021-Refinement/report.tex
more comments

@@
 % TODO: give a context, a circuit cannot block physical time from progressing
+\Ludo{TODOludo}{lire l explication quand elle y sera}
 \begin{figure}
@@
 
-When expanding the aliases \(S, i, V\) in the definition, and remarking that the last existential quantifier can be unfolded into a transition in \(A\) and one in \(A_p\) with the added condition that they match, the definition become mildly similar with the deadlock reduction one.
+When expanding the aliases \(S, i, V\) in \Ludo{the definition}{which def?
+pas lu la suite car je savais pas ou ca allait}, and remarking that the last existential quantifier can be unfolded into a transition in \(A\) and one in \(A_p\) with the added condition that they match, the definition become mildly similar with the deadlock reduction one.
 It is not a coincidence because their goal is to caracterise the same kind of compatibility between automata.
@@
 \[ \forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \to \values, \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \]
+\Ludo{Question}{on the composed side you might have more variables, eg communicated by the sub-automata or by a sub-hole or stored in the state, how are they quantified?}
 \end{defi}

### 2021-05-06 2021-Refinement/report.tex
Paid half of lemma1 proof debt

--- 2021-05-06 2021-Refinement/report.tex
@@
 An open transition can have many unbound variable, actually an effective transition of the automaton is any well-formed substitution of the unbound variables of the transition minus the automaton variables.
-This is used to constrain the infinite branching to be representable, making it possible to reason about.
+% This is used to constrain the infinite branching to be representable, making it possible to reason about.
 
@@
 We can proceed to explain the left enable operator example.
-The automata on the left side is \(\OA{\mbrc{L, R}}{L}{\emptyset}{\mbrc{}}{\mbrc{l, r}}{T}\) where transitions in \(T\) are generated by
+The automata on the left side is \(\OA{\mbrc{L, R}}{L}{\emptyset}{\mbrc{}}{\mbrc{l, r}}{T}\) where transitions in \(T\) are:
 \begin{align*}
@@
 \end{align*}
+\vspace{-1cm}
 \begin{gather*}
-	\fvars{\OTg} \defnotation \mpar{\fvars{\alpha} \cup \fvars{g} \cup \bigcup_{j \in J'} \fvars{\beta_j} \cup \bigcup_{v \in V} \fvars{\psi\mpar{v}}} \setminus V \\
-	\fguard{\OTg} \defnotation g
+	\fguard{\OTg} \defnotation g \\
+	\fvars{\OTg} \defnotation \mpar{\fvars{\alpha} \cup \fvars{g} \cup \bigcup_{j \in J'} \fvars{\beta_j} \cup \bigcup_{v \in V} \fvars{\psi\mpar{v}}} \setminus V
 \end{gather*}
@@
 The drawing introduces the double arrows which is used to denote the initial valuation.
-The automata drawn is \(\OA{\mbrc{\_}}{\_}{\mbrc{v}}{l^\mbrc{v}}{\mbrc{l, r}}{T}\) where transitions in \(T\) are like previously all the transitions generated by
+The automata drawn is \(\OA{\mbrc{\_}}{\_}{\mbrc{v}}{l^\mbrc{v}}{\mbrc{l, r}}{T}\) where transitions in \(T\) are:
 \begin{align*}
@@
 
-The variables of a transition are all the free variables in the expressions minus the auomaton variables.
+The variables of a transition are all the free variables in the expressions minus the automaton variables.
 For instance \(v\) is a variable name for the automaton which is used in the guard.
@@
 \begin{exi}
-This example is derived and adapted from a traffic light controller in a collection of examples for pNets.
-It is supposed to be a single traffic light.
-
-Figure \ref{fig:tls} shows the light controller with some synchronisation logic.
-It  takes an unimplemented control circuit in the hole \(ctl\) which gives the timings and an also unimplemented counter in the hole \(cnt\) to count external \(\act{tick}\) actions.
-The three states are used to remember which colored light is on and this color can be retrieved by the environment by synchronising with the actions \(\act{onXxx}\) (Xxx is either Red, Yellow or Green) if it is not stored externally.
-
-The color switches when the register and the control circuit agree that the time is over.
-The new time limit can be set by the control circuit and the exposed action to the exterior is a \(\tau\).
-
 \begin{figure}
@@
 \end{figure}
+This example is derived and adapted from a traffic light controller in a collection of examples for pNets.
+It is supposed to be a single traffic light.
+
+Figure \ref{fig:tls} shows the light controller with some synchronisation logic.
+It  takes an unimplemented control circuit in the hole \(ctl\) which gives the timings and an also unimplemented counter in the hole \(cnt\) to count external \(\act{tick}\) actions.
+The three states are used to remember which colored light is on and this color can be retrieved by the environment by synchronising with the actions \(\act{onXxx}\) (Xxx is either Red, Yellow or Green) if it is not stored externally.
+
+The color switches when the register and the control circuit agree that the time is over.
+The new time limit can be set by the control circuit and the exposed action to the exterior is a \(\tau\).
+
 The component we choose to compose in the holes are in Figure \ref{fig:tlh}.
@@
 
+\begin{figure}
+\centering
+\input{Traffic_Lights_Full.tex}
+\caption{The full traffic lights system}
+\label{fig:tlf}
+\end{figure}
 The automaton on Figure \ref{fig:tlf} is bisimilar to the composition of the specification on Figure \ref{fig:tls} and the agents on Figure \ref{fig:tlh}.
@@
 
-\begin{figure}
-\centering
-\input{Traffic_Lights_Full.tex}
-\caption{The full traffic lights system}
-\label{fig:tlf}
-\end{figure}
 To illustrate composition, simplification and value passing, the \(\tau\) transition from the state \(R\) will be examined.
@@
 
-The relations will have to be at least preorders, simulations and \Ludo{introduction of deadlocks}{define more precisely introduction of deadlocks or refer to a future definition} (state where no transition is possible) to be called refinement simulation.
+The relations will have to be at least preorders, simulations and forbid the introduction of deadlocks (state where no transition is possible) to be called refinement simulation.
 On top of that weak refinement are refinement where some actions, typically one named \(\tau\), are considered not observable and can occur in the implementation while not having to be matched in the specification.
 In the weak refinement the relations have to forbid the introduction of livelocks (only a sequence of \(\tau\) possible) and respect \(\tau\)-stuttering \marginpar{cite many things arround here}.
-\Ludo{to add}{I believe we want more arguments on why we want some properties, at least deadlock and livelock related, perhaps also weak vs strong.
-How did you decide of the list of useful properties / when ais such or such property useful?}
-
 While being preorder is simple to express for a relation, being a simulation, do not introduce new deadlocks/livelocks and \(\tau\)-stuttering are properties about the states of the related automata, therefore they are more complex to express.
@@
 
-Two states \(s_1 \in S_1, s_2 \in S_2\) are related under a \Ludo{?}{relation is mission: under a relation $R$ for a valuation ...
-?} valuation \(\sigma: V_1 \uplus V_2 \to \values\) iff \(\sigma \vdash R\mpar{s_1, s_2}\).
+Two states \(s_1 \in S_1, s_2 \in S_2\) are related under a valuation \(\sigma: V_1 \uplus V_2 \to \values\) iff \(\sigma \vdash R\mpar{s_1, s_2}\).
 For a relation \(\wrel{}{}{}\) which uses a relation under predicate to prove that two element are related \(\forall x \, x', x \wrel{}{}{} x' \iff \exists R, P\mpar{R}\), the fact that there is a valid witness \(R\) is noted \(\wrel{x}{x'}{R}\).
@@
 \begin{defi}[Simulation on open automata]
-A relation \(\leq\) is a simulation if for any two related automata \(\wrel{A_1}{A_2}{R}\) where \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\), \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and \(R: S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\), \(R\) satisfies both
+A relation \(\leq\) is a simulation if for any related automata \(\wrel{A_1}{A_2}{R}\) where \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\), \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and \(R: S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\), \(R\) satisfies both
 \defitem Initial states are related under initial valuations: \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\);
-\defitem From related states, all out-transitions from \(A_1\) can be simulated in \(A_2\) and their target states are \Ludo{related}{I am a bit surprised that $J_1$ and $J_2$ are unrelated and we only need to take only the intersection TBD}:
+\defitem From related states, all out-transitions from \(A_1\) can be simulated in \(A_2\) and their target states are related:
 \begin{multline*}
@@
 The last formula means that for every pair of related states under valuation of the automaton variables and every possible transitions (\(\vdash g_1\)) from the first automaton, there is a possible transition (\(\vdash g_2\)) such that the produced action matches (\(\alpha_1 = \alpha_2\)), the holes actions from same hole names (\(J'_1 \cap J'_2\)) match (\(\beta_{1j} = \beta_{2j}\)) and the target states are related after variable update.
-This is a natural extension of the notion of simulation on LTS, which is the same definition without variables and holes and guards.
+This is a natural extenion of the notion of simulation on LTS, which is the same definition without variables and holes and guards.
 It will serve as a watchdog for any relation that will be defined with ``simulation" in its name, except weak-simulation where the transition from the first automaton that produce \(\tau\) actions are excluded.
@@
 \end{defi}
-This definition \Ludo{extends the requirements of a simulation}{je suis pas d accord avec cette affirmation, ou tout du moins c est pas evident} by requiring from the relation that on related states, either there is a pair of possible matching transition or there was no out-transition possible in the specification.
+This definition extends the requirements of a simulation by requiring from the relation that on related states, either there is a pair of possible matching transition or there was no out-transition possible in the specification.
 This requirement effectively prevents the presence of deadlock state in the first automaton if there is a related non-deadlock state in the second.
@@
 ``Deadlock reduction" conflicts with ``composition completeness" by disallowing some unwanted cases where an automaton in a hole cannot produce any action that any out-transitions expects.
-In particular filling a hole with the deadlock automaton (only one state without out-transitions) is not considered a refinement for a \Ludo{no deadlock reducing simulation refinement}{define or use the name of the definition}.
-A way to solve this \Ludo{issue}{why is this an issue?
-can be solved by stating which properties are desirable for which reason above} is to characterise a composition that do not introduce deadlocks, which will be used instead of the composition introduced earlier.
+In particular filling a hole with the deadlock automaton (only one state without out-transitions) is not considered a refinement for a no deadlock reducing simulation refinement.
+A way to solve this issue is to caracterise a composition that do not introduce deadlocks, which will be used instead of the composition introduced earlier.
 \begin{defi}[Reachability]
@@
 \end{defi}
-
 For the reader not used to simulations and bisimulations, this definition of a predicate can seem strange.
-The reachability predicate is used to characterise the states and valuations that are reachable in a run of an automaton.
-In fact the role of the predicate is to characterise potentially reachable configurations without having to characterise the fact that the state and valuation are the result of a valid path in an automaton.
+The reachability predicate is used to caracterise the states and valuations that are reachable in a run of an automaton.
+In fact the role of the predicate is to caracterise potentially reachable configurations without having to caracterise the fact that the state and valuation are the result of a valid path in an automaton.
 
@@
 This effectively makes reachability account for all paths and potentially over-approximate the reachable configurations.
-However the exact reachability may not be reprensentable in the formulae, hence the need of potentially over-approximating.
+However the exact rechability may not be reprensentable in the formulae, hence the need of potentially over-approximating.
 
@@
 \begin{defi}[Non-locking composition, intuitive definition]
-
-The composition  \(A_p\subst{A_c}{k} = \OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(A_c \defobject \OA{S_c}{s_{0c}}{V_c}{\sigma_{0c}}{J_c}{T_c}\), \(A_p \defobject \OA{S_p}{s_{0p}}{V_p}{\sigma_{0p}}{J_p}{T_p}\) and \(k \in J_p\), is a non-locking composition if there is a reachability predicate such that from reachable configurations, either a transition is possible in \(A_p\subst{A_c}{k}\) or there were no possible transition in \(A_p\) to begin with
+The composition resulting in \(A_p\subst{A_c}{k} = \OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(A_c \defobject \OA{S_c}{s_{0c}}{V_c}{\sigma_{0c}}{J_c}{T_c}\), \(A_p \defobject \OA{S_p}{s_{0p}}{V_p}{\sigma_{0p}}{J_p}{T_p}\) and \(k \in J_p\), is a non-locking composition if there is a rechability predicate such that from reachable configurations, either a transition is possible in \(A_p\subst{A_c}{k}\) or there were no possible transition in \(A_p\) to begin with
 \begin{multline*}
@@
 
-To illustrate the introduction of a deadlock in a composition and the definition of non-locking composition, we consider the following example.
+To illustrate the introduction of a deadlock in a composition and the definition of non-locking composition, let's look at an example.
 \begin{exi}[Deadlocks introduced by composition]
@@
 
-\begin{defi}[Deadlock reduction, working definition]
+\begin{defi}[Deadlock reduction, working definition] % TODO HERE: Maybe there is a union vars OT(s_2) missing in the domain of sigma
 A simulation \(\leq\) is deadlock reducing if in all the \(R: S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\) such that \(\wrel{A_1}{A_2}{R}\), there is one that also satisfies
-\[ \forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \to \values, \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \]
+\begin{multline*}
+	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \uplus \bigcup_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values, \\
+	\sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
+\end{multline*}
 \end{defi}
@@
 The composition \(A \defobject A_p\subst{A_c}{k}\) is a non-locking composition if:
-\[ \forall s \in S, \forall \sigma: V \to \values, \sigma \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
+\[ \forall s \in S, \forall \sigma: V \uplus \bigcup_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values, \sigma \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
 \end{defi}
@@
 \section{Proof of equivalent definitions}\label{apx:lemeqd}
-\begin{proof}[Lemma 1] % TODO HERE: Always introduce hypothesis and goals on a big math env, recall definitions (also simulation) and call hypothesis H1, H2, ...
-Let \(R, A_1, A_2\) be such that \(\wrel{A_1}{A_2}{R}\).
+\begin{proof}[Lemma 1]
+Let \(R\), \(A_1 \defobject \OA{S_1}{s_{01}}{V_1}{\sigma_{01}}{J_1}{T_1}\), \(A_2 \defobject \OA{S_2}{s_{02}}{V_2}{\sigma_{02}}{J_2}{T_2}\) be such that:
+\[ \wrel{A_1}{A_2}{R} \hyp{0} \]
 We want to prove:
-\begin{gather*}
-	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \to \values, \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \\
-\iff \\
+\begin{multline}
+	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \uplus \bigcup_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values, \\
+	\sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \tag{WD}\label{eq:WD}
+\end{multline}
+\[ \iff \]
+\begin{multline}
 	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V \to \values, \mpar{\sigma \vdash R\mpar{s_1, s_2}} \implies \\
@@
 	\end{array}} \\
-	\vee \forall t_2 \in \fOT{s_2}, \forall \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \nvdash \fguard{t_2}
-\end{gather*}
-\item[\(\implies\):] If \(R\) satisfies the deadlock reduction definition, let \(\mpar{s_1, s_2} \in S_1 \times S_2\).
+	\vee \forall t_2 \in \fOT{s_2}, \forall \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \nvdash \fguard{t_2} \tag{ID}\label{eq:ID}
+\end{multline}
+\item[\bf(\ref{eq:WD})\(\implies\)(\ref{eq:ID}):]
+	Let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \(\sigma: V \to \values\) be such that:
+	\[ \sigma \vdash R\mpar{s_1, s_2} \hyp{1} \]
+	By excluded middle, either the right hand side of the disjunction in (\ref{eq:WD}) holds, in which case the property holds, or it is false and we have the hypothesis:
+	\[ \exists t_2 \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \vdash \fguard{t_2} \hyp{2} \]
+	We get immediately the values \(t_2\), \(\nu\) and the hypothesis:
+	\[ \sigma \uplus \nu \vdash \fguard{t_2} \hyp{2'} \]
+	\(R\) satisfies (\ref{eq:WD}) with the current value of \(\mpar{s_1, s_2}\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \(\bigcup_{t_2 \in \fOT{s_2}} \fguard{t_2}\) so we have:
+	\[ \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{3} \]
+	The \(\vdash\) hides an implicit \(\exists\) that we use to get values to the variables in \(\bigcup_{t_1 \in \fOT{s_1}}\) in a valuation \(\mu\).
+	The left side of the implication is proved using \hyp{1} and \hyp{2'} for the branch \(t_2\) of the disjunction.
+	We are now allowed to decompose the right side to get \(t_1\) such that:
+	\[ \sigma \uplus \nu \uplus \mu \vdash \fguard{t_1} \hyp{3'} \]
+	At this point we have a \(t_1\) and a \(t_2\) so we may think that the proof is about to be finished because the only property left to prove is:
+	\begin{multline}
+		\bigsymb{\exists} \OTx{2}{}{2}{2} \in \fOT{s_2}, \OTx{1}{}{1}{1} \in \fOT{s_1}, \\
+		\sigma \vdash g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_1 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \goal{1}
+	\end{multline}
+	However we cannot yet prove it because we don't know whether \(t_2\) and \(t_1\) do match.
+	In order to get a \(t_2\) matching \(t_1\) we use will use \hyp{0}.
+	\hyp{0} with current value of \(\mpar{s_1, s_2}\), \(t_1\) and \(\sigma \uplus \mu\) as a valuation of \(V_1 \uplus V_2 \uplus \fvars{t_1}\) gives:
+	\begin{multline}
+		\mpar{\sigma \uplus \mu \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \exists t_2 \defobject \OTx{2}{}{2}{} \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \\
+		\sigma \uplus \mu \uplus \nu \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \hyp{0'}
+	\end{multline}
+	The left part of the implication is \hyp{1} and \hyp{3'}, so we get \(t'_2 \in \fOT{s_2}\), \(\nu': \fvars{t_2} \to \values\) and:
+	\[ \sigma \uplus \mu \uplus \nu' \vdash \alpha_1 = \alpha'_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J''_2} \beta_{1j} = \beta'_{2j} \wedge g'_2 \wedge R\mpar{s'_1, s''_2}\psubst{\psi_1 \uplus \psi'_2} \hyp{target} \]
+	The witnesses for \goal{1} are \(t'_2\) and \(t_1\), and the rest is proved with a combination of \hyp{target} and \hyp{3'}.
+\item[\bf(\ref{eq:WD})\(\impliedby\)(\ref{eq:ID}):] % TODO: proof debt, restart here
+	If \(R\) satisfies the equivalent formula, let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \(\sigma: V_1 \uplus V_2 \to \values\).
 	The free variables of the equivalent formula are all in \(V_1 \uplus V_2\) so let \(\sigma: V_1 \uplus V_2 \to \values\) be such that
@@
 	Now we can decompose \hyp{E} to get \(t_1 \in T_1\), which we know is also in \(\fOT{s_1}\), a transition that we won't use and \(\sigma \vdash \fguard{t_1}\) which is what we needed to prove the branch \(t_1\) of \goal{G1}.
-\item[\(\impliedby\):] If \(R\) satisfies the equivalent formula, let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \(\sigma: V_1 \uplus V_2 \to \values\).
-	Let admit that there is a transition \(t_2 \in T_2\) such that \hyp{g2}: \(\sigma \vdash R\mpar{s_1, s_2} \wedge \fguard{t_2}\).
-	We need to prove \goal{G1}:
-	\[ \bigsymb{\exists} \OTx{2}{}{2}{2} \in T_2, \OTx{1}{}{1}{1} \in T_1, \sigma \vdash g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_1 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \]
-	We use the fact that \(R\) satisfies the equivalent formula with the current value of \(s_1, s_2\) and \(\sigma\) to get
-	\[ \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \]
-	As this formula is true for all values of each free variable, it is especially true when valuated with \(\sigma\).
-	We know that \(t_2 \in \fOT{s_2}\) so \hyp{g2} proves the left part of that implication and we immediately decompose the right side to get \(t_1 \in \fOT{s_1}\) and \hyp{g1}: \(\fguard{t_1}\).
-
-	We cannot yet prove \goal{G1} because at this point we don't know whether \(t_2\) and \(t_1\) do match.
-	In order to get a matching \(t_2\) we use the fact that \(R\) is also witness of the simulation \(A_1 \leq A_2\) with the current value of \(s_1, s_2, \sigma\) and \(t_1\) as \hyp{sim}:
-	\[ \mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} \OTx{2}{}{2}{2} \in T_2, \sigma \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \]
-	The left part of the implication is the left side of \hyp{g2} so we get \(t'_2 \in T_2\) and what's after as the hypothesis \hyp{target}.
-	The witnesses for \goal{G1} are \(t'_2\) and \(t_1\), and the rest is proved with a combination of \hyp{target} and \hyp{g1}.
 \end{proof}

### 2021-05-06 2021-Refinement/report.tex

@@
 
-To illustrate the introduction of a deadlock in a composition and the definition of non-locking composition, let's look at an example.
+To illustrate the introduction of a deadlock in a composition and the definition of non-locking composition, we consider the following example.
 \begin{exi}[Deadlocks introduced by composition]
 % TODO: give a context, a circuit cannot block physical time from progressing
+\Ludo{TODOludo}{lire l explication quand elle y sera}
 \begin{figure}
@@
 
-\begin{defi}[Deadlock reduction, working definition] % TODO HERE: Maybe there is a union vars OT(s_2) missing in the domain of sigma
+\begin{defi}[Deadlock reduction, working definition]
 A simulation \(\leq\) is deadlock reducing if in all the \(R: S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\) such that \(\wrel{A_1}{A_2}{R}\), there is one that also satisfies
@@
 \end{multline*}
+\Ludo{Question}{on the composed side you might have more variables, eg communicated by the sub-automata or by a sub-hole or stored in the state, how are they quantified?}
+\Quentin{Merge-conflict}{I edited the formula above before reading your message, is your question still relevant?}
 \end{defi}

### 2021-05-07 2021-Refinement/report.tex
Comments again (commented out figure to be able to compile)

@@
 \end{multline*}
-\Ludo{Question}{on the composed side you might have more variables, eg communicated by the sub-automata or by a sub-hole or stored in the state, how are they quantified?}
-\Quentin{Merge-conflict}{I edited the formula above before reading your message, is your question still relevant?}
+\Ludo{New Question}{what is the meaning of sigma here: it is not used on the right hand side of the implication; this seem to mean if there is  a sigma such that s1 and s2 are related then we have thr peoperty on disujunction on pred qithout caring about the valuation.
+Am I right?
+same question for the def below}
 \end{defi}
@@
 In the parallel case the condition is checked after the parallel substitution because there is no guarantee that any order of sequential composition is non-locking for every substitution even if the parallel substitution is non-locking.
-\begin{exi} % TODO
-\begin{figure}
-\centering
-\input{}
-\vrule
-\input{}
-\vrule
-\input{}
-\caption{}
-\label{fig:pnls}
-\end{figure}
+%\begin{exi} % TODO
+%\begin{figure}
+%\centering
+%\input{}
+%\vrule
+%\input{}
+%\vrule
+%\input{}
+%\caption{}
+%\label{fig:pnls}
+%\end{figure}
 An example of non-locking parallel substitution where no individual substitution is non-locking is given in Figure \ref{fig:pnls}.% TODO HERE
-\end{exi}
+%\end{exi}
 From this point and in the previous definitions, composition will only refer to non-locking composition.
@@
 \section{Preliminary refinement relations}\label{sec:prelref}
+\Ludo{organisation}{Is this only preliminaries, if yes could it be placed earlier? if no perhaps rename into refinement for open automata something}
 The main goal of this section is to help the reader understand the problems, constraints and different elements involved to solve them so that they are not all introduced at once in the real refinement relation.
-The main objective of the refinement relations in this section is to be able to say that a composition of two automata is a refinement of the base automaton (\(a\mbrk{b} \leq a\)) in restricted interesting cases.
+The main objective of the refinement relations \Ludo{in this section}{du coup la on se pose la question est ce juste ici ou est ce le but global, c est quio le schema general?
+ceci dit ca sera peut etre resolu par l introduction ...
+mais dans tous les cas une petite couche sur ou on est et ou on va ca serait bien.
+il faut quelque part clairemetn definir ce qu on veut et sous quelle condition plus tot que ici} is to be able to say that a composition of two automata is a refinement of the base automaton (\(a\mbrk{b} \leq a\)) in restricted interesting cases.
+\Ludo{lost}{I do not understand the last sentence}
 Hopefully they can be used as simpler (and less expensive) versions of the real refinement relation in the case the manipulated automata respect the constraints.
 
-Composing an open automaton can give an automaton where not much can be said in terms of hole indicies.
+Composing an open automaton can give an automaton where the holes of the obtained automatonn cannot be relatd with the holes of the original one.
 So looking at restricted cases where holes are related in a specific manner can help understanding the general case.
-For two open automata \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), the following refinement relations are defined.
 
+For two open automata \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), we first define a refinement relation where holes of the compared automata are identical.
 This relation is the basis for all the other ones.
-It applies on automaton with same holes.
-The goal is to caracterise open automata that have a more determined (more deterministic) behaviour without adding deadlocks.
+The goal is to characterise open automata that have a more determined (more deterministic) behaviour without adding deadlocks.
+This corresponds to ????
+in the classical definitions of refinement \\Ludo{TODO}{j imagine que rabea peut donner des refs ici}
 \begin{defi}[Hole-identical refinement] % TODO: transition variables
@@
 
-The specificities of open automata comes in when relating the (initial) states.
-The relation \(R\) relates \(i_1\) to \(i_2\) under the condition that the curent value of variables satisfies \(R\mpar{i_1, i_2}\).
+The specificities of open automata at on the relation between the (initial) states.
+\Ludo{lost}{When reading the next sentences I am not sure where we are going, what is notation introduction of concepts or definitions, please clarify}
+The relation \(R\) relates \(i_1\) to \(i_2\) under the condition that the current value of variables satisfies \(R\mpar{i_1, i_2}\).
 If two states \(s_1 \in S_1, s_2 \in S_2\) are not(/never) related then \(\nvdash R\mpar{s_1, s_2}\).
@@
 This is already used in FH-bisimulation introduced in previous articles about open automata.
+\Ludo{OK}{I guess I understand that you want to reach the next sentence as an explanation of the notations used in the definition, I mainly believe it is necessary to re-organise the ideas before}
 So the meaning of \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\) is that the initial states with the initial valuation are effectively related.
+\newpage % TODO: remove when less comments :)
+
 \begin{defi}[Hole-identical simulation]
-\Quentin{``\(R\) is a hole-identical simulation of \(A_1\) in \(A_2\)"}{Any idea on how to note that? \(R \vDash A_1 \leq_= A_2\) for instance.} is defined as: % TODO: \wrel
+\Quentin{``\(R\) is a hole-identical simulation of \(A_1\) in \(A_2\)"}{Any idea on how to note that?
+\(R \vDash A_1 \leq_= A_2\) for instance.} \Ludo{reply}{I believe the notation  \(R \vDash A_1 \leq_= A_2\) is not bad bbut for the text I would rather write a1 is a simulation of a2 according to (as witnessed by) R ???} is defined as: % TODO: \wrel
 \begin{multline*}
@@
 The first two lines quantify on source states, transitions (and target states) and source states valuations.
-The 3\textsuperscript{rd} line is the condition to ensure that transitions are not matched to incompatible ones:
-For all variable assignement of the two automata and all hole actions (quantification of \(\sigma\)), assuming that the states were related and the transition in \(A_1\) is possible (\(R\mpar{s_1, s_2} \wedge g_1\) part) then there is always a transition, not necessarily only one, which can be performed (\(g_{2x}\)), produce the same action (\(\alpha_1 = \alpha_{2x}\)), accept the same action from the holes (\(\beta_{1j} = \beta_{2xj}\)) and satisfy the predicate for relating the target states after variable update (\(R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\)).
+The \Ludo{3\textsuperscript{rd}}{is this the good line number?} line is the condition to ensure that transitions are not matched to incompatible ones:
+For all variable assignments of the two automata and all hole actions (quantification of \(\sigma\)), assuming that the states were related and the transition in \(A_1\) is possible (\(R\mpar{s_1, s_2} \wedge g_1\) part) then there is always a set of transitions, not necessarily only one as several transitions might simulate the same one depending on the value of variables for example; these transitions can be performed (\(g_{2x}\)), produce the same action (\(\alpha_1 = \alpha_{2x}\)), accept the same action from the holes (\(\beta_{1j} = \beta_{2xj}\)) and satisfy the predicate for relating the target states after variable update (\(R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\)).
 
-The notion of refinement here is stating that \(A_1\) is a refinement of \(A_2\) if \(A_1\) can be simulated in \(A_2\).
-The hole-identical part is referring to the fact that holes indicies are the same and identical holes indicies have to perform the same actions.
-On top of that the last line ensures no deadlock introduction.
-It can be interpreted ``assuming the predicate holds and there is any possible transition in \(A_2\) (= no deadlock), then there must be a possible transition in \(A_1\) (= no deadlock)".
+The notion of refinement here is stating that \(A_1\) is a refinement of \(A_2\) if \(A_1\) can be simulated \Ludo{in}{by?} \(A_2\).
+The hole-identical part is referring to the fact that holes indices are the same and identical holes indices have to perform the same actions.
+On top of that the last line ensures that no deadlock is introduced.
+It can be interpreted ``assuming the predicate holds and there is any possible transition in \(A_2\) (= no deadlock), then there must be a possible transition in \(A_1\) (= no deadlock)''.
 It does not have to ensure that this transition isn't garbage or that the target states are related because the first part of the simulation already does it.
-Also if there was a deadlock then there is no transition because no trasition can be simulated in a deadlock, that's why it is more a deadlock equivalence than a deadlock reduction.
+Also if there was a deadlock then there is no transition because no transition can be simulated in a deadlock, that's why it is more a deadlock equivalence than a deadlock reduction.\Ludo{?}{the last sentence is not very clear}
 
@@
 \end{lem}
-The first property is one part of the hole-identical simulation, the second property is the central part of the refinement simulation requirement.
+The first property is one part of the hole-identical simulation, the second property is the central part of the \Ludo{refinement simulation requirement}{add reference to def}.
 If we prove the direct way of this equivalence and \(\leq_=\) is a preorder then \(\leq_=\) is a refinement simulation.
 The other way is there because I hope that it will be easier to use this formulation to prove that \(\leq_=\) is a preorder. % Will need to be modified
-One may wonder why it was not used in the definition if it is equivalent.
-The reason is that the formulation used is compatible with SMT solver, the place where it will most probably be used in practise.
+\Ludo{One may wonder why it was not used}{rephrase and state in what sense this second one could be considered as better} in the definition if it is equivalent.
+The reason is that the formulation used in definition??? is compatible with SMT solver, the place where it will most probably be used in practise.
 \begin{proof} Let \(\mpar{s_1, s_2} \in S_1 \times S_2\),
@@
 	\end{multline*}
-	Unfolding the definition of \(\sigma \vdash f\) where \(f\) is not a closed formula in \(H_{smt}\) gives an exists that we use to get \nmm{\nu: \biguplus_{x \in X} \fvars{t_{2x}} \to \values} and
+	\Ludo{Unfolding the definition}{I really cannot understand this step you will need to explain us I believe, and add details here.
+TODOLudo: read the rest of the proof after explanation} of \(\sigma \vdash f\) where \(f\) is not a closed formula in \(H_{smt}\) gives an exists that we use to get \nmm{\nu: \biguplus_{x \in X} \fvars{t_{2x}} \to \values} and
 	\[ H_{valid} \defobject \sigma \uplus \nu \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}

### 2021-05-07 2021-Refinement/report.tex
Finished cleaning proof for lemma 1

--- 2021-05-06 2021-Refinement/report.tex
@@
 \begin{multline*}
-	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V \to \values, \mpar{\sigma \vdash R\mpar{s_1, s_2}} \implies \\
+	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \to \values, \mpar{\sigma \vdash R\mpar{s_1, s_2}} \implies \\
 	\mpar{\everymath{\displaystyle}\begin{array}{c}
@@
 \begin{multline}
-	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V \to \values, \mpar{\sigma \vdash R\mpar{s_1, s_2}} \implies \\
+	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \to \values, \mpar{\sigma \vdash R\mpar{s_1, s_2}} \implies \\
 	\mpar{\everymath{\displaystyle}\begin{array}{c}
@@
 \item[\bf(\ref{eq:WD})\(\implies\)(\ref{eq:ID}):]
-	Let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \(\sigma: V \to \values\) be such that:
+	Let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \(\sigma: V_1 \uplus V_2 \to \values\) be such that:
 	\[ \sigma \vdash R\mpar{s_1, s_2} \hyp{1} \]
@@
 	The witnesses for \goal{1} are \(t'_2\) and \(t_1\), and the rest is proved with a combination of \hyp{target} and \hyp{3'}.
-\item[\bf(\ref{eq:WD})\(\impliedby\)(\ref{eq:ID}):] % TODO: proof debt, restart here
-	If \(R\) satisfies the equivalent formula, let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \(\sigma: V_1 \uplus V_2 \to \values\).
-	The free variables of the equivalent formula are all in \(V_1 \uplus V_2\) so let \(\sigma: V_1 \uplus V_2 \to \values\) be such that
-	\[ \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \]
-	We can decompose it by admitting the left part of the implication then decomposing the big disjunction to get \(\sigma \vdash R\mpar{s_1, s_2}\) as \hyp{p} and \(t_2 \in \fOT{s_2}\) such that \hyp{g2}: \(\sigma \vdash \fguard{t_2}\).
-	We are left to prove \[ \sigma \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{G1} \]
-	To do that we will use the fact that \(R\) satisfies the deadlock reduction definition with the current value of \(s_1, s_2, \sigma\).
-	Now we additionally need to prove \goal{G2}: \(\exists t_2 \in \fOT{s_2}, \sigma \vdash R\mpar{s_1, s_2} \wedge \fguard{t_2}\) before getting hypothesis \hyp{E}:
-	\[ \bigsymb{\exists} \OTx{2}{}{2}{2} \in T_2, \OTx{1}{}{1}{1} \in T_1, \sigma \vdash g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_1 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \]
-	The witness of \goal{G2} is \(t_2\) obtained previously in the big disjunction, and \(\sigma \vdash R\mpar{s_1, s_2} \wedge \fguard{t_2}\) is proved by combining \hyp{p} and \hyp{g2}.
-	Now we can decompose \hyp{E} to get \(t_1 \in T_1\), which we know is also in \(\fOT{s_1}\), a transition that we won't use and \(\sigma \vdash \fguard{t_1}\) which is what we needed to prove the branch \(t_1\) of \goal{G1}.
+\item[\bf(\ref{eq:WD})\(\impliedby\)(\ref{eq:ID}):]
+	Let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \(\sigma: V_1 \uplus V_2 \uplus \bigcup_{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values\).
+	We want to prove:
+	\[ \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{1} \]
+	We can admit the left part of the implication in which we decompose the big disjunction to get \(t_2 \in \fOT{s_2}\) and:
+	\begin{align*}
+		\sigma \vdash R\mpar{s_1, s_2} & \text{ \hyp{1}} &
+		\sigma \vdash \fguard{t_2} & \text{ \hyp{2}}
+	\end{align*}
+	We are left to prove:
+	\[ \sigma \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{1'} \]
+	To do that we use (\ref{eq:ID}) with the current value of \(\mpar{s_1, s_2}\) and \(\sigma\), and prove the premisse of the implication with \hyp{1} to get:
+	\begin{multline}
+		\mpar{\everymath{\displaystyle}\begin{array}{c}
+			\bigsymb{\exists} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_1} \uplus \fvars{t_2} \to \values, \\
+			\sigma \uplus \nu \vdash g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
+		\end{array}} \\
+		\vee \forall t_2 \in \fOT{s_2}, \forall \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \nvdash \fguard{t_2} \hyp{3}
+	\end{multline}
+	There are two cases in this disjunction, the second is in contradiction with \hyp{2} and the first gives \(t_1\), \(t'_2\) and \(\nu\) such that (only the interesting part of the conjunction has been extracted):
+	\[ \sigma \uplus \nu \vdash \fguard{t_1} \hyp{4} \]
+	Which proves \goal{1'} with the values of \(\nu\) for the variables of \(\fguard{t_1}\) and dummy values for the other guards.
 \end{proof}
 
-% TODO
+\begin{proof}[Lemma 2]
+% TODO: recall what we want to prove, then prove it
+\end{proof}
 

### 2021-05-10 2021-Refinement/report.tex
Proof for Lemma 2

@@
 \end{defi}
+(\(\pi_X\) is the projection of tuples on \(X\)).
 
@@
 \begin{exi}[Deadlocks introduced by composition]
-% TODO: give a context, a circuit cannot block physical time from progressing
-\Ludo{TODOludo}{lire l explication quand elle y sera}
+\Ludo{TODOludo}{lire l'explication}
+This example reuses the counter introduced in Figure \ref{fig:tlh}.
+The behaviour of the counter is to count external \(\act{tick}\) actions up to the amount set by action \(\act{set}\mpar{x}\) then to notify the environnement that this amount of time elapsed.
+In the traffic light example the clock is not specified, we will introduce deadlocks using a wisely choosen clock specification.
+However the full traffic light will not be used in order to simplify the example, only the counter will be.
+
 \begin{figure}
@@
 \end{figure}
-% TODO: explain
+The clock on the left side of Figure \ref{fig:anytick} transmit the actions of its hole unchanged until the clock imposes a \(\act{tick}\) on its hole.
+This can model a physical clock, because physical time ticks cannot be delayed.
+
+If the hole cannot register a \(\act{tick}\) at any time then there is a deadlock, which is the case with our counter.
+The composition of this clock with the counter is given on the left of Figure \ref{fig:deadlock}.
 \begin{figure}
@@
 \end{figure}
-% TODO: explain
+There are two deadlocks:
+The first is in the state \(1S\), which correspond to the clock trying to imppose a tick when the counter is not set.
+The second is in the state \(1C\), which correspond to the clock trying to impose a tick when the counter has reached the amount peviously set, but not has not yet reported it to the environment.
+These deadlocks could have been in the specification in which case they were intended, but it is not the case here.
+
+The counter on the right of Figure \ref{fig:anytick} is a modification to accept ticks at in any state.
+Composing this modified counter gives the automaton on the right of Figure \ref{fig:deadlock} which has no deadlocks.
+
+We should successfully caracterise the second composition as non-locking but fail for the first.
+In the state \(0S\) any valuation is reachable (no initial valuation).
+In both automata the transition \nmm{\OT{0S}{1S}{\tau}{\mbrc{}}{\top}{\mbrc{}}} has a true guard, hence the first branch of the disjunction holds.
+In the state \(0C\) % TODO: run the definition of non-locking composition
 \end{exi}
@@
 The composition \(A \defobject A_p\subst{A_c}{k}\) is a non-locking composition if:
-\[ \forall s \in S, \forall \sigma: V \uplus \bigcup_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values, \sigma \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
+\[ \forall s \in S, \forall \sigma: V \uplus \bigcup_\subbox{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fvars{t_p} \to \values, \sigma \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
 \end{defi}
@@
 \end{figure}
-An example of non-locking parallel substitution where no individual substitution is non-locking is given in Figure \ref{fig:pnls}.% TODO HERE
+An example of non-locking parallel substitution where no individual substitution is non-locking is given in Figure \ref{fig:pnls}.% TODO
 \end{exi}
@@
 	As a valuation for variables in \(\fvars{t_{2x}}\) we have \(\nu\), so \(H_{target}\mpar{x}\) concludes the proof.
-\item[\(\impliedby\):] We admit the bottom formula as \(H_{ref}\), let \(t_1 \defobject \OTx{1}{}{1}{} \in T_1\) % TODO HERE; quantify on all valuations to get t_{2\sigma}
+\item[\(\impliedby\):] We admit the bottom formula as \(H_{ref}\), let \(t_1 \defobject \OTx{1}{}{1}{} \in T_1\) % TODO; quantify on all valuations to get t_{2\sigma}
 \end{proof}
@@
 \section{Proof of equivalent definitions}\label{apx:lemeqd}
-\begin{proof}[Lemma 1]
+\begin{proof}[Proof of lemma 1]
 Let \(R\), \(A_1 \defobject \OA{S_1}{s_{01}}{V_1}{\sigma_{01}}{J_1}{T_1}\), \(A_2 \defobject \OA{S_2}{s_{02}}{V_2}{\sigma_{02}}{J_2}{T_2}\) be such that:
@@
 	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \uplus \bigcup_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values, \\
-	\sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \tag{WD}\label{eq:WD}
+	\sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \tag{WD}\label{eq:drWD}
 \end{multline}
@@
 	\end{array}} \\
-	\vee \forall t_2 \in \fOT{s_2}, \forall \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \nvdash \fguard{t_2} \tag{ID}\label{eq:ID}
+	\vee \forall t_2 \in \fOT{s_2}, \forall \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \nvdash \fguard{t_2} \tag{ID}\label{eq:drID}
 \end{multline}
-\item[\bf(\ref{eq:WD})\(\implies\)(\ref{eq:ID}):]
+\item[\bf(\ref{eq:drWD})\(\implies\)(\ref{eq:drID}):]
 	Let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \(\sigma: V_1 \uplus V_2 \to \values\) be such that:
 	\[ \sigma \vdash R\mpar{s_1, s_2} \hyp{1} \]
-	By excluded middle, either the right hand side of the disjunction in (\ref{eq:WD}) holds, in which case the property holds, or it is false and we have the hypothesis:
+	By excluded middle, either the right hand side of the disjunction in (\ref{eq:drWD}) holds, in which case the property holds, or it doesn't hold and we have the hypothesis:
 	\[ \exists t_2 \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \vdash \fguard{t_2} \hyp{2} \]
@@
 	\[ \sigma \uplus \nu \vdash \fguard{t_2} \hyp{2'} \]
-	\(R\) satisfies (\ref{eq:WD}) with the current value of \(\mpar{s_1, s_2}\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \(\bigcup_{t_2 \in \fOT{s_2}} \fguard{t_2}\) so we have:
-	\[ \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{3} \]
+	\(R\) satisfies (\ref{eq:drWD}) with the current value of \(\mpar{s_1, s_2}\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \(\bigcup_{t_2 \in \fOT{s_2}} \fguard{t_2}\) so we have:
+	\[ \sigma \uplus \nu \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{3} \]
 	The \(\vdash\) hides an implicit \(\exists\) that we use to get values to the variables in \(\bigcup_{t_1 \in \fOT{s_1}}\) in a valuation \(\mu\).
@@
 	The witnesses for \goal{1} are \(t'_2\) and \(t_1\), and the rest is proved with a combination of \hyp{target} and \hyp{3'}.
-\item[\bf(\ref{eq:WD})\(\impliedby\)(\ref{eq:ID}):]
+\item[\bf(\ref{eq:drWD})\(\impliedby\)(\ref{eq:drID}):]
 	Let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \(\sigma: V_1 \uplus V_2 \uplus \bigcup_{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values\).
@@
 	\[ \sigma \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{1'} \]
-	To do that we use (\ref{eq:ID}) with the current value of \(\mpar{s_1, s_2}\) and \(\sigma\), and prove the premisse of the implication with \hyp{1} to get:
+	To do that we use (\ref{eq:drID}) with the current value of \(\mpar{s_1, s_2}\) and \(\sigma\), and prove the premisse of the implication with \hyp{1} to get:
 	\begin{multline}
@@
 
-\begin{proof}[Lemma 2]
-% TODO: recall what we want to prove, then prove it
+\begin{proof}[Proof of lemma 2]
+\[ \forall s \in S, \forall \sigma: V \uplus \bigcup_\subbox{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fvars{t_p} \to \values, \sigma \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \tag{WD}\label{eq:nlcWD} \]
+\[ \iff \]
+\begin{multline*}
+	\forall s \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A}\mpar{s}} \implies \mpar{\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t}} \\
+	\vee \forall t_p \in \fOT{\pi_{S_p}\mpar{s}}, \forall \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \nvdash \fguard{t_p} \tag{ID}\label{eq:nlcID}
+\end{multline*}
+\item[\bf(\ref{eq:nlcWD})\(\implies\)(\ref{eq:nlcID}):]
+	Let \(s \in S\) and \(\sigma \in V \to \values\) be such that:
+	\[ \sigma \vdash \reach{A}\mpar{s} \hyp{1} \]
+	By excluded middle, either the right hand side of the disjunction in (\ref{eq:nlcWD}) holds, in which case the property holds, or it doesn't hold and we have the hypothesis:
+	\[ \exists t_p \in \fOT{\pi_{S_p}\mpar{s}}, \exists \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \vdash \fguard{t_p} \hyp{2} \]
+	We get immediately the values \(t_p\), \(\nu\) and the hypothesis:
+	\[ \sigma \uplus \nu \vdash \fguard{t_p} \hyp{2'} \]
+	\(R\) satisfies (\ref{eq:nlcWD}) with the current value of \(s\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \(\bigcup_{t_p \in \fOT{\pi_{s_p}\mpar{s}}} \fguard{t_p}\) so we have:
+	\[ \sigma \uplus \nu \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{3} \]
+	The \(\vdash\) hides an implicit \(\exists\) that we use to get values to the variables in \(\bigcup_{t \in \fOT{s}}\) in a valuation \(\mu\).
+	The left side of the implication is proved using \hyp{1} and \hyp{2'} for the branch \(t_p\) of the disjunction.
+	We are now allowed to decompose the right side to get \(t\) such that:
+	\[ \sigma \uplus \nu \uplus \mu \vdash \fguard{t} \hyp{3'} \]
+	At this point we have a \(t\) which is composed of a transition in \(A_p\) and one in \(A_c\) so unlike lemma 1 we do not need to check that two transitions matches.
+	The current goal is:
+	\[ \exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t} \]
+	Which is proved on \(t\) with valuation \(\mu\) by \hyp{3'}.
+\item[\bf(\ref{eq:nlcWD})\(\impliedby\)(\ref{eq:nlcID}):]
+	Let \(s \in S\), \(\sigma \in V \uplus \bigcup_{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fvars{t_p} \to \values\).
+	We want to prove:
+	\[ \sigma \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \goal{1} \]
+	We can admit the left part of the implication in which we decompose the big disjunction to get \(t_p\) and:
+	\begin{align*}
+		\sigma \vdash \reach{A}\mpar{s} & \text{ \hyp{1}} &
+		\sigma \vdash \fguard{t_p} & \text{ \hyp{2}}
+	\end{align*}
+	We are left to prove:
+	\[ \sigma \vdash \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \goal{1'} \]
+	To do that we use (\ref{eq:nlcID}) with the current value of \(s\) and \(\sigma\), and prove the premisse of the implication with \hyp{1} to get:
+	\begin{multline}
+		\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t} \\
+		\vee \forall t_p \in \fOT{\pi_{S_p}\mpar{s}}, \forall \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \nvdash \fguard{t_p} \hyp{3}
+	\end{multline}
+	There are two cases in this disjunction, the second is in contradiction with \hyp{2} and the first gives \(t\) and \(\nu\) such that:
+	\[ \sigma \uplus \nu \vdash \fguard{t} \hyp{4} \]
+	Which proves \goal{1'} with the values of \(\nu\) for the variables of \(\fguard{t}\) and dummy values for the other guards.
 \end{proof}

### 2021-05-10 2021-Refinement/report.tex

@@
 In the parallel case the condition is checked after the parallel substitution because there is no guarantee that any order of sequential composition is non-locking for every substitution even if the parallel substitution is non-locking.
-\begin{exi} % TODO
-\begin{figure}
-\centering
-\input{}
-\vrule
-\input{}
-\vrule
-\input{}
-\caption{}
-\label{fig:pnls}
-\end{figure}
-An example of non-locking parallel substitution where no individual substitution is non-locking is given in Figure \ref{fig:pnls}.% TODO
-\end{exi}
+%\begin{exi} % TODO
+%\begin{figure}
+%\centering
+%\input{}
+%\vrule
+%\input{}
+%\vrule
+%\input{}
+%\caption{}
+%\label{fig:pnls}
+%\end{figure}
+An example of non-locking parallel substitution where no individual substitution is non-locking is given in Figure \ref{fig:pnls}.% TODO HERE
+%\end{exi}
 From this point and in the previous definitions, composition will only refer to non-locking composition.

### 2021-05-11 2021-Refinement/report.tex
Non locking composition explained

@@
 The initial valuation may be a partial valuation of the variables, if the undefined variables are set before being read this behave like a normal variable.
-If the undefined variable is not set before being read then its value may be any fixed value, the potential use of this construct will be explain in more details in section ???\marginpar{refinement section, hole identical is sufficient for the parametric construct}.
+If the undefined variable is not set before being read then its value may be any fixed value, the potential use of this construct will be explain in more details in Section \ref{sec:prelref}.
 \begin{defi}[Open transition]
@@
 We should successfully caracterise the second composition as non-locking but fail for the first.
-In the state \(0S\) any valuation is reachable (no initial valuation).
+\begin{itemize}
+\item In the state \(0S\) any valuation is reachable (no initial valuation).
 	In both automata the transition \nmm{\OT{0S}{1S}{\tau}{\mbrc{}}{\top}{\mbrc{}}} has a true guard, hence the first branch of the disjunction holds.
-In the state \(0C\) % TODO: run the definition of non-locking composition
+\item In the state \(0C\), for the left automaton, valuations where \(t \geq c \geq 0 \vee \mpar{t < 0 \wedge c = 0}\) are reachable; for the right automaton, valuations where \(c \geq 0\) are reachable.
+	For all these valuations the transition \nmm{\OT{0C}{1C}{\tau}{\mbrc{}}{\top}{\mbrc{}}} has a true guard, hence the first branch of the disjunction holds.
+\item In the state \(1C\), the same valuations as the ones reachable in \(0C\) are also reachable.
+	In the right automaton the transition \nmm{\OT{1C}{0C}{\act{tick}}{\mbrc{}}{\top}{\mbrc{c \gets c + 1}}} has a true guard.
+	In the left automaton the transition \nmm{\OT{1C}{0C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} covers the cases where \(c < t\).
+	For the other cases (\(c = t \vee t \leq 0 \mbrk{\leq c}\)) there are no transition with a true guard, and in the clock the transition same transition as for the state \(1S\) has a true guard, hence the composition is not non-locking.
+\item In the state \(1S\) any valuation is reachable.
+	In the left automaton, no transition is possible, and in the parent automaton \nmm{\OT{1}{0}{\act{tick}}{\mbrc{H \mapsto \act{tick}}}{\top}{\mbrc{}}} had a true guard, so the composition is not a non-locking composition (we already know it at this point).
+	In the right automaton, \nmm{\OT{1S}{0S}{\act{tick}}{\mbrc{}}{\top}{\mbrc{}}} has a true guard.
+\end{itemize}
+The left automaton indeed fails at being the result of a non-locking composition where the right automaton passes.
+
+One more thing worth noting is that for the left automaton, in the state \(1C\) with a valuation such that \(t < 0\), the counter agent is in a deadlock state.
+We could have defined the non-locking composition so that this is considered as an intended deadlock, making the requirement symetric.
+However the the semantic of composition in a hole is assymetric and the considered specification -as in the deadlock reduction- is the parent automaton.
+A symetric version is presented in Section ???\marginpar{TODO LATER}, where we introduce a more symetric model of open automata.
 \end{exi}

### 2021-05-11 2021-Refinement/report.tex
Added TODOs

@@
 
-The relations will have to be at least preorders, simulations and \Ludo{introduction of deadlocks}{define more precisely introduction of deadlocks or refer to a future definition} (state where no transition is possible) to be called refinement simulation.
+The relations will have to be at least preorders, simulations and prevent the introduction of deadlocks to be called refinement simulation.
+Deadlocks are states and valuations that are reachable in a run and from which no further transition is possible.
 On top of that weak refinement are refinement where some actions, typically one named \(\tau\), are considered not observable and can occur in the implementation while not having to be matched in the specification.
@@
 
-Two states \(s_1 \in S_1, s_2 \in S_2\) are related under a \Ludo{?}{relation is mission: under a relation $R$ for a valuation ...
-?} valuation \(\sigma: V_1 \uplus V_2 \to \values\) iff \(\sigma \vdash R\mpar{s_1, s_2}\).
+Two states \(s_1 \in S_1, s_2 \in S_2\) with their respective valuations \(\sigma_1: V_1 \to \values, \sigma_2: V_2 \to \values\) are related iff \(\sigma_1 \uplus \sigma_2 \vdash R\mpar{s_1, s_2}\).
 For a relation \(\wrel{}{}{}\) which uses a relation under predicate to prove that two element are related \(\forall x \, x', x \wrel{}{}{} x' \iff \exists R, P\mpar{R}\), the fact that there is a valid witness \(R\) is noted \(\wrel{x}{x'}{R}\).
@@
 ``Deadlock reduction" conflicts with ``composition completeness" by disallowing some unwanted cases where an automaton in a hole cannot produce any action that any out-transitions expects.
-In particular filling a hole with the deadlock automaton (only one state without out-transitions) is not considered a refinement for a \Ludo{no deadlock reducing simulation refinement}{define or use the name of the definition}.
+In particular filling a hole with the deadlock automaton (only one state without out-transitions) is not considered a refinement for a \Ludo{deadlock reducing simulation refinement}{define or use the name of the definition}.
 A way to solve this \Ludo{issue}{why is this an issue?
@@
 \end{defi}
-(\(\pi_X\) is the projection of tuples on \(X\)).
+(\(\pi_X\) is the projection of tuples on the set \(X\)). % TODO: Move that to the notations
 
@@
 
-When expanding the aliases \(S, i, V\) in \Ludo{the definition}{which def?
+When expanding the aliases \(S, s_0, V\) in \Ludo{the definition}{which def?
 pas lu la suite car je savais pas ou ca allait}, and remarking that the last existential quantifier can be unfolded into a transition in \(A\) and one in \(A_p\) with the added condition that they match, the definition become mildly similar with the deadlock reduction one.
+% TODO: Make it clearer, what expansion, what is the result; or remove
 It is not a coincidence because their goal is to caracterise the same kind of compatibility between automata.
@@
 same question for the def below}
+\Quentin{Reply}{Any variable not defined by the valuation is under an implicit \(\exists\) quantifier (satisfiability).
+What it means is that for every valuation where states are related and a transition is possible (disjunction on the left), there is a value for the free variables of the disjunction on the right that makes a transition possible (the existential quantifier has been wisely displaced in this explaination to make it easier to understand).}
 \end{defi}
+% TODO: Explain this formulations (it will also do the job of explaining the definition below)
 \begin{lem}
@@
 
-\section{Preliminary refinement relations}\label{sec:prelref}
+\section{Refinement relations in restricted cases}\label{sec:prelref}
 \Ludo{organisation}{Is this only preliminaries, if yes could it be placed earlier? if no perhaps rename into refinement for open automata something}
@@
 mais dans tous les cas une petite couche sur ou on est et ou on va ca serait bien.
-il faut quelque part clairemetn definir ce qu on veut et sous quelle condition plus tot que ici} is to be able to say that a composition of two automata is a refinement of the base automaton (\(a\mbrk{b} \leq a\)) in restricted interesting cases.
+il faut quelque part clairemetn definir ce qu on veut et sous quelle condition plus tot que ici} is to be able to state that a composition of two automata is a refinement of the base automaton (\(a\mbrk{b} \leq a\)) in restricted interesting cases.
+% TODO: probably remove, this is was written when the previous section was not yet written
 \Ludo{lost}{I do not understand the last sentence}
@@
 The goal is to characterise open automata that have a more determined (more deterministic) behaviour without adding deadlocks.
-This corresponds to ????
-in the classical definitions of refinement \\Ludo{TODO}{j imagine que rabea peut donner des refs ici}
+This corresponds to ???? in the classical definitions of refinement \Ludo{TODO}{j imagine que rabea peut donner des refs ici}.
 \begin{defi}[Hole-identical refinement] % TODO: transition variables
@@
 So the meaning of \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\) is that the initial states with the initial valuation are effectively related.
+% TODO: Also a relic of the past, when things were explained on the go instead of in a dedicated section.
+Remove if already explained, move otherwise
 \newpage % TODO: remove when less comments :)
@@
 \Quentin{``\(R\) is a hole-identical simulation of \(A_1\) in \(A_2\)"}{Any idea on how to note that?
-\(R \vDash A_1 \leq_= A_2\) for instance.} \Ludo{reply}{I believe the notation  \(R \vDash A_1 \leq_= A_2\) is not bad bbut for the text I would rather write a1 is a simulation of a2 according to (as witnessed by) R ???} is defined as: % TODO: \wrel
+\(R \vDash A_1 \leq_= A_2\) for instance.} \Ludo{reply}{I believe the notation  \(R \vDash A_1 \leq_= A_2\) is not bad bbut for the text I would rather write a1 is a simulation of a2 according to (as witnessed by) R ???} is defined as: % TODO: Actually this was already answered, \wrel is the settled way
 \begin{multline*}

### 2021-05-12 2021-Refinement/report.tex
Sync

@@
 \defitem The precedence of \(\vdash\) is the lowest on the right side and higher than \(\uplus\) on the left side:
-\[ \forall a \, b, a \uplus b \vdash x \wedge y \implies \exists z, P\mpar{x,z} \text{ is the same as } \forall a \, b, \mpar{\mpar{a \uplus b} \vdash \mpar{\mpar{x \wedge y} \implies \exists z, P\mpar{x,z}}} \]
+\[ \forall a \, b, a \uplus b \vdash x \wedge y \implies \exists z, P\mpar{x,z} \text{ is the same as } \forall a \, b, \mpar{\mpar{a \uplus b} \vdash \mpar{\mpar{x \wedge y} \implies \exists z, P\mpar{x,z}}} \] % Mettre des niveaux de parenthèses
 \end{noti}
@@
 \defitem \textbf{compatible with composition} iff \(\forall a\, b\, c\, d, a \leq b \wedge c \leq d \implies c\mbrk{a} \leq d\mbrk{b}\);
-\defitem \textbf{compatibile with FH-bisimulation} iff \(\forall a\, b\, c, d, a \overset{FH}= b \wedge c \overset{FH}= d \wedge a \leq c \implies b \leq d\).
+\defitem \textbf{compatible with FH-bisimulation} iff \(\forall a\, b\, c, d, a \overset{FH}= b \wedge c \overset{FH}= d \wedge a \leq c \implies b \leq d\).
 \end{defi}
@@
 Now the properties about states of automata can be adapted to open automata.
-\begin{defi}[Simulation on open automata]
+\begin{defi}[Simulation on open automata] % TODO: faire une définition standard
 A relation \(\leq\) is a simulation if for any two related automata \(\wrel{A_1}{A_2}{R}\) where \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\), \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and \(R: S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\), \(R\) satisfies both
@@
 \defitem From related states, all out-transitions from \(A_1\) can be simulated in \(A_2\) and their target states are \Ludo{related}{I am a bit surprised that $J_1$ and $J_2$ are unrelated and we only need to take only the intersection TBD}:
-\begin{multline*}
+\begin{multline*} % Mettre des sets de noms en commun qu'on veut effectivement mapper pour la transitivité
 	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \forall \sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values, \\
@@
 In particular filling a hole with the deadlock automaton (only one state without out-transitions) is not considered a refinement for a \Ludo{deadlock reducing simulation refinement}{define or use the name of the definition}.
+% Unfold a little bit and remove refinement
 A way to solve this \Ludo{issue}{why is this an issue?
 can be solved by stating which properties are desirable for which reason above} is to characterise a composition that do not introduce deadlocks, which will be used instead of the composition introduced earlier.
+% Issue référence le conflit mais ce n'est pas clair, clarifie ça, replace issue with conflict
 \begin{defi}[Reachability]
@@
 	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \uplus \bigcup_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values, \\
-	\sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
+	\sigma \vdash \mpar{R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
 \end{multline*}
-\Ludo{New Question}{what is the meaning of sigma here: it is not used on the right hand side of the implication; this seem to mean if there is  a sigma such that s1 and s2 are related then we have thr peoperty on disujunction on pred qithout caring about the valuation.
-Am I right?
-same question for the def below}
-\Quentin{Reply}{Any variable not defined by the valuation is under an implicit \(\exists\) quantifier (satisfiability).
-What it means is that for every valuation where states are related and a transition is possible (disjunction on the left), there is a value for the free variables of the disjunction on the right that makes a transition possible (the existential quantifier has been wisely displaced in this explaination to make it easier to understand).}
 \end{defi}
@@
 \section{Refinement relations in restricted cases}\label{sec:prelref}
-\Ludo{organisation}{Is this only preliminaries, if yes could it be placed earlier? if no perhaps rename into refinement for open automata something}
 The main goal of this section is to help the reader understand the problems, constraints and different elements involved to solve them so that they are not all introduced at once in the real refinement relation.
@@
 \Ludo{lost}{I do not understand the last sentence}
-Hopefully they can be used as simpler (and less expensive) versions of the real refinement relation in the case the manipulated automata respect the constraints.
+Hopefully they can be used as simpler (and less expensive) versions of the real refinement relation in the case the manipulated automata respect some constraints.
 
@@
 If two states \(s_1 \in S_1, s_2 \in S_2\) are not(/never) related then \(\nvdash R\mpar{s_1, s_2}\).
-The predicate \(R\mpar{i_1, i_2}\) is used to take into account the fact that a state is also constituted of the value of the variables.
+The predicate \(R\mpar{s_{01}, s_{02}}\) is used to take into account the fact that a state is also constituted of the value of the variables.
 This is already used in FH-bisimulation introduced in previous articles about open automata.
@@
 It does not have to ensure that this transition isn't garbage or that the target states are related because the first part of the simulation already does it.
-Also if there was a deadlock then there is no transition because no transition can be simulated in a deadlock, that's why it is more a deadlock equivalence than a deadlock reduction.\Ludo{?}{the last sentence is not very clear}
+Also if there was a deadlock then there is no transition because no transition can be simulated in a deadlock.
+In that regard deadlock reduction caracterises in fact the absence of deadlock creation.\Ludo{?}{the last sentence is not very clear}
 
@@
 \end{lem}
-The first property is one part of the hole-identical simulation, the second property is the central part of the \Ludo{refinement simulation requirement}{add reference to def}.
+The first property is one part of the hole-identical simulation, the second property is the central part of the \Ludo{refinement simulation requirement}{add reference to def (like "def x")}.
 If we prove the direct way of this equivalence and \(\leq_=\) is a preorder then \(\leq_=\) is a refinement simulation.
 The other way is there because I hope that it will be easier to use this formulation to prove that \(\leq_=\) is a preorder. % Will need to be modified
-\Ludo{One may wonder why it was not used}{rephrase and state in what sense this second one could be considered as better} in the definition if it is equivalent.
+\Ludo{One may wonder why it was not used}{rephrase and state in what sense this second one could be considered as better} in the definition if it is equivalent. % Informal!
 The reason is that the formulation used in definition??? is compatible with SMT solver, the place where it will most probably be used in practise.

### 2021-05-15 2021-Refinement/Traffic_Lights_Spec.tex
Checked up to section 5

@@
 \draw (v1) edge[dir=150] node[left] {\OTd{\act{onRed}}{}{}} (v1);
-\draw (v1) edge[dir=80] node[above] {\OTd{\tau}{ctl \mapsto \theta\mpar{x}, cnt \mapsto \act{set}\mpar{x}}{}} (v1);
+\draw (v1) edge[dir=80] node[above] {\OTd{\tau}{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}{}} (v1);
 \draw (v1) edge node {\OTd{\act{TurnGreen}}{cnt \mapsto \act{over}\mpar{x}, ctl \mapsto \delta\mpar{x}}{}} (v2);
@@
 \draw (v2) edge[dir=30] node[right] {\OTd{\act{onGreen}}{}{}} (v2);
-\draw (v2) edge[dir=320] node[xshift=1cm,below] {\OTd{\tau}{ctl \mapsto \theta\mpar{x}, cnt \mapsto \act{set}\mpar{x}}{}} (v2);
+\draw (v2) edge[dir=320] node[xshift=1cm,below] {\OTd{\tau}{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}{}} (v2);
 \draw (v2) edge node[pos=0.6] {\OTd{\act{TurnYellow}}{cnt \mapsto \act{over}\mpar{x}, ctl \mapsto \delta\mpar{x}}{}} (v3);
@@
 \draw (v3) edge[dir=270] node {\OTd{\act{onYellow}}{}{}} (v3);
-\draw (v3) edge[dir=200] node {\OTd{\tau}{ctl \mapsto \theta\mpar{x}, cnt \mapsto \act{set}\mpar{x}}{}} (v3);
+\draw (v3) edge[dir=200] node {\OTd{\tau}{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}{}} (v3);
 \draw (v3) edge node[pos=0.4] {\OTd{\act{TurnRed}}{cnt \mapsto \act{over}\mpar{x}, ctl \mapsto \delta\mpar{x}}{}} (v1);

### 2021-05-15 2021-Refinement/report.tex
Checked up to section 5

@@
 \usetikzlibrary{external}
-% \usepackage{hyperref}
+\usepackage[colorlinks]{hyperref}
 % \usepackage{xcolor}
@@
 % transitions between sections
+% TODO: CITER LES CONFERENCES
 
@@
 \section{Introduction}
-The model of open automata is used to give the semantic of open pNets \cite{2007.10770}.
-Open pNets are not petri nets but an intermediate representation used in the VerCors project to perform verification and model checking \cite{henrio:01252323}.
-Open pNets with the open automaton semantic and equivalence relation introduced in previous work \cite{2007.10770} were sucessfully used to verify BIP and GCM \cite{qin:01823507, ameurboulifa:01526055}.
-However equivalences relations are not sufficient to perform model checking, refinement relations are also used.
+The open automata model is used to give the semantic of open pNets \cite{2007.10770}.
+Open pNets are not petri nets but an intermediate representation used in the VerCors project to perform verification \cite{henrio:01252323}.
+Verification is the process of checking that an implementation satisfies a specification.
+Open pNets with the open automaton semantics and equivalence relation introduced in previous work \cite{2007.10770} were sucessfully used to model and verify BIP and GCM \cite{qin:01823507, ameurboulifa:01526055}.
+However equivalences relations are not always sufficient to perform verification, refinement relations are also used.
 For instance an example of open pNet where equivalence is not sufficient was encountered in ...\marginpar{Paper where the motivating example came up}.
 
-In this article we introduce a refinement relation for open automata\marginpar{TODO: expand}.
+The contributions of this article are the definition of composition for open automata without having to define open pNets, and the introduciton of several refinement relations for open automata\marginpar{TODO: expand}.
 
-We begin in section \ref{sec:notations} by giving some notations used throughout this paper.
+We begin with Section \ref{sec:notations} by giving some notations used throughout this paper.
 Then there are several sections dedicated to define all the interesting objects and properties:
-In section \ref{sec:def} we give a clean and up to date definition of open automata.
-In section \ref{sec:semcompo} we recall the semantic for open automata and their composition without requiring the use of open pNets.
-In section \ref{sec:proofelts} we adapt the standard properties related to refinement relation from LTS to open automata.
-After that the section \ref{sec:prelref} is dedicated to progressively build a refinement relation.
-Finally the section \ref{sec:refinement} introduces and analyses the refinement relation on open automata.
+In Section \ref{sec:def} we give a clean and up to date definition of open automata.
+In Section \ref{sec:comp} we define their composition without requiring the use of open pNets.
+In Section \ref{sec:proofelts} we adapt the standard properties related to refinement relation from LTS to open automata.
+After that Section \ref{sec:prelref} is dedicated to progressively build a refinement relation.
+Section \ref{sec:refinement} introduces and analyses the refinement relation on open automata.
+% flat model
+% future work
+% conclusion
 
@@
 
-Throughout this paper, tuples might be noted differently depending on what they represent.
+Throughout this paper, tuples will be noted differently depending on what they represent.
+This helps distinguishing the manipulated objects.
+Every such notation will be introduced in the definition of the object.
 
-Family of values, or equivalently maps will be noted \(\mset{i \mapsto x_i}{i \in I}\), \(\mset{i \gets x_i}{i \in I}\) or \(x_i^{i \in I}\).
-The latter will only be used when there is a generating expression; for instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\).
-However \(\mbrc{\alpha \mapsto 1, \beta \mapsto 2, \gamma \mapsto 3}\) has no generating expression and is represented with the first notation in a finite context.
+Families of values, or equivalently maps will be noted \(\mset{i \mapsto x_i}{i \in I}\), \(\mset{i \gets x_i}{i \in I}\) or \(x_i^{i \in I}\).
+The latter can only be used if there is a generating expression; for instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\).
+However \(\mbrc{\alpha \mapsto 1, \beta \mapsto 2, \gamma \mapsto 3}\) has no generating expression and is represented here with the finite version of first notation.
 The disjoint union of two maps \(\varphi: I \to X\) and \(\psi: J \to Y\) with \(I \cap J = \emptyset\) is \(\varphi \uplus \psi: I \uplus J \to X \cup Y\).
@@
 
-\section{Open Automaton}\label{sec:def}
-To define an open automaton we need some preliminary definitions.
-\begin{defi}[Expression algebra, Action algebra, Formulae, Terms]
-An expression algebra \(E\) is a disjoint union \(E \defobject \terms \uplus \actions \uplus \formulae\) of the terms, the actions and the formulae.
+\section{Open Automata}\label{sec:def}
+To define the open automata we need some preliminary definitions.
+\begin{defi}[Expression algebra, Action algebra, Formulas, Terms]
+An expression algebra \(E\) is a disjoint union \(E \defobject \terms \uplus \actions \uplus \formulas\) of the terms, the actions and the formulas.
 
-The terms \(\terms\) is a term algebra.
-The action algebra \(\actions\) is the set of pairs \(\labels \times \terms\) where \(\labels\) are the action labels.
-The formulae \(\formulae\) are at least the first order formulae over \(\terms\) and \(\labels\).
+The terms \(\terms\) is a term algebra\marginpar{reference to come}.
+As any term algebra it has constant symbols with arity, variables, and a typing mechanism to distinguish well-formed and ill-formed terms.
+The action algebra \(\actions\) is another term algebra.
+It can be a subset of the terms.
+The formulas \(\formulas\) are at least the first order formulas over \(\terms\) and \(\actions\).
 \end{defi}
-The term algebra and action labels are arbitrary.
-An element \(\mpar{l, t} \in \actions\) is noted \(l\mpar{t}\).
-The formulae contain at least first order logic terms with an equality relation.
-This equality relation is not necessarily a syntactic equality (\(2 + 2 \neq 4\) with a syntactic equality) on \(\terms\).
+The term algebras are arbitrary.
+The formulas contain at least first order logic terms with an equality relation.
+This equality relation is not necessarily a syntactic equality (\(2 + 2 \neq 4\) with a syntactic equality).
 
-An example of term algebra can be Peano integers (zero, variable and successor function), the formulae associated can use equality relation, the sum relation \(\mathit{sum}\mpar{a, b, c} \defobject a = b + c\) and the product relation \(\mathit{prod}\mpar{a, b, c} \defobject a = b \times c\).
+An example of term algebra can be Peano integers (constant zero with arity 0, constant successor function with arity 1 and the variables), the formulas associated can use syntactic equality relation, the sum relation \(\mathit{sum}\mpar{a, b, c}: \text{``}a = b + c\text{"}\) and the product relation \(\mathit{prod}\mpar{a, b, c}: \text{``}a = b \times c\text{"}\).
 
-\begin{defi}[Free variables, Closed terms, Closed formulae]
-\defitem \(\fvars{e}\) is the set of unbound variables in \(e \in E\).
+\begin{defi}[Unbound variables, Expressions restricted to variables, Closed expressions]
+\defitem \(\fvars{e}\) is the set of variables in \(e \in E\) that are not bound by any binder.
+	Binders can be for instance quantifiers in formulas, or let-binders in terms if they are part of the term algebra.
 \defitem The expressions restricted to variables in \(V\) are \(E_V \defnotation \mset{e \in E}{\fvars{e} \subseteq V}\); \(E_V \subset E\).
@@
 \end{defi}
-Terms, actions and formulae restricted to variables and their closed versions are also defined by restriction.
-A closed expression can contain variables, only unbound variable are restricted.
+Terms, actions and formulas restricted to variables and their closed versions are also defined by restriction.
+A closed expression can contain variables under a binder, only unbound variable are forbidden.
 
 We can use the previous example of first order formula on Peano integers to illustrate these definitions.
-\(x\), \(S\mpar{y}\) are valid terms, \(0\) is a closed term, \(\fvars{x} = \mbrc{x}\), \(\fvars{S\mpar{y}} = \mbrc{y}\), \(\fvars{0} = \emptyset\).
-\(x = 0\), \(\forall y, \exists x, \mathit{sum}\mpar{y, z, x}\) are valid formulae, \(\forall x, \neg S\mpar{x} = 0\) is a valid closed formula, \(\fvars{x = 0} = \mbrc{x}\), \(\fvars{\forall y, \exists x, \mathit{sum}\mpar{y, z, x}} = \mbrc{z}\), \(\fvars{\forall x, \neg S\mpar{x} = 0} = \emptyset\).
+\(x\), \(S\mpar{y}\) are well-formed terms, \(0\) is a closed term, \(\fvars{x} = \mbrc{x}\), \(\fvars{S\mpar{y}} = \mbrc{y}\), \(\fvars{0} = \emptyset\).
+\(x = 0\), \(\forall y, \exists x, \mathit{sum}\mpar{y, z, x}\) are valid formulas, \(\forall x, \neg S\mpar{x} = 0\) is a valid closed formula, \(\fvars{x = 0} = \mbrc{x}\), \(\fvars{\forall y, \exists x, \mathit{sum}\mpar{y, z, x}} = \mbrc{z}\), \(\fvars{\forall x, \neg S\mpar{x} = 0} = \emptyset\).
 
-\begin{defi}[Interpretation, Values, Satisfiability, (Parallel) substitution]
+\begin{defi}[Values, Satisfiability, (Parallel) substitution]
 We assume that the following are given:
 \defitem The values \(\values\), which are interpretations of closed terms.
-\defitem The satisfiability relation on closed formulae, \({\vdash} \subseteq \rformulae\).
+\defitem The satisfiability relation on closed formulas, \({\vdash} f\) where \(f \in \rformulas\).
 \defitem The substitution in \(e \in E\) of \(x \in \fvars{e}\) by \(t \in \terms\), \(e\subst{t}{x}\).
@@
 For the parallel substitution, the set \(V\) is not required to be a subset of \(\fvars{e}\).
-In the case where it is not, the variables in \(V \setminus \fvars{e}\) are not substituted.
+In the case it isn't, the variables in \(V \setminus \fvars{e}\) are not substituted.
 The substitutions might give a ill-formed expression; for instance let the terms be integers and pairs with (pointwise) addition, \(\mpar{a + b}\psubst{a \mapsto 7, b \mapsto \mpar{4, 5}}\) is a ill-formed term.
@@
 The interpretation of terms is supposed to be decidable.
-The satisfiability of formulae might not be decidable nor complete nor consistent, however we will pretend like they are because these are really hard problems for logicians that we don't want to deal with.
+The satisfiability of formulas might not be decidable nor complete nor consistent, however we will pretend like they are because these are really hard problems for logicians that we don't want to deal with.
 For instance a formula with quantifiers on variables might not be provable even if it is true for all values of these variables.
-In practise the formulae will be given to a SMT solver and we make sure they have all the previous properties.
-Actually \(\vdash\) is used to separate the external logic and the logic on \(\formulae\).
+In practise the formulas will be given to a SMT solver and we cannot always make sure they have all the previous properties.
+\(\vdash\) can hence be interpreted as an indicator of what is given to the SMT; it separates the external logic and the logic on \(\formulas\).
 
@@
 This is correct when \(\values \subseteq \rterms\) and we suppose it is the case.
-Otherwise it doesn't invalidates theorem because it can stand as a shorthand for substitution with any term which is interpreted as \(v\).
+Otherwise it doesn't invalidates theorems because it can stand as a shorthand for substitution with any term which is interpreted the kept value.
 We suppose that the interpretation of terms is compatible w.r.t.\@ substitution, that is if two terms \(t\), \(t'\) are interpreted with the same value, then replacing \(t\) by \(t'\) in a well-formed expression makes an equivalent well-formed expression.
-\begin{noti}[Notations for separating external logic and logic on \(\formulae\)]
-\defitem The satisfiability relation will be noted using the classical relational notation \(\vdash f\).
-\defitem The satisfiability of a formula \(f \in \formulae\) under some valuation \(\sigma: V \to \values\) is noted:
+\begin{noti}[Notations for separating external logic and logic on \(\formulas\)]
+\defitem The satisfiability of a formula \(f \in \formulas\) under some valuation \(\sigma: V \to \values\) is noted:
 \[ \sigma \vdash f \defnotation \vdash \exists \fvars{f\psubst{\sigma}}, f\psubst{\sigma} \]
-\defitem The satisfiability of a formula \(f \in \formulae\) with some variable set \(V\) as context is noted:
+\defitem The satisfiability of a formula \(f \in \formulas\) with some variable set \(V\) as context is noted:
 \[ V \vdash f \defnotation \vdash \forall V, \exists\mpar{\fvars{f} \setminus V}, f \]
 \defitem The precedence of \(\vdash\) is the lowest on the right side and higher than \(\uplus\) on the left side:
-\[ \forall a \, b, a \uplus b \vdash x \wedge y \implies \exists z, P\mpar{x,z} \text{ is the same as } \forall a \, b, \mpar{\mpar{a \uplus b} \vdash \mpar{\mpar{x \wedge y} \implies \exists z, P\mpar{x,z}}} \] % Mettre des niveaux de parenthèses
+\[ \forall a \, b, a \uplus b \vdash x \wedge y \implies \exists z, P\mpar{x,z} \text{ is the same as } \forall a \, b, \bigg((a \uplus b) \vdash \Big((x \wedge y) \implies \exists z, P\mpar{x,z}\Big)\bigg) \]
 \end{noti}
@@
 
-\(S, V, J\) are arbitrary finite sets.
+\(S, V, J\) are arbitrary finite sets. % OR finite arbitrary sets?
 \end{defi}
-The variable names may clash when considering two automata, in that case we suppose that we can still distinguish the variables in the formulas.
-% The open transitions will be considered to be a finite set of representative open transitions. Removing this restriction may break some theorems.
-The initial valuation may be a partial valuation of the variables, if the undefined variables are set before being read this behave like a normal variable.
-If the undefined variable is not set before being read then its value may be any fixed value, the potential use of this construct will be explain in more details in Section \ref{sec:prelref}.
+The variable names may clash when considering two automata, in this case we suppose that we can still distinguish the variables in the formulas.
+In practise the open automata are used in a toolchain at a point where what came before guarantees there are no name clash, which is why we make this assumption.
+
+The initial valuation may be a partial valuation of the variables.
+If an undefined variable is set before being read, it behaves like an initially set variable.
+If an undefined variable is not set before being read then its value may be any fixed value.
+When refining the automaton it can be set by the implementation, or it can be left unspecified as a parameter of the automaton (for instance a \(n\) bits register has \(n\) as parameter).
 \begin{defi}[Open transition]
-An open transition is a tuple \nmm{\OTg} with \(s, s' \in S\) the source and target states, \(\alpha \in \actions\) the produced action, \(J' \subseteq J\) the holes involved, \(\beta_j \in \actions\) the actions of the holes, \(g \in \rformulae\) the guard and \(\psi: V \to \terms\) the new value of the variables.
+An open transition is a tuple \nmm{\OTg} with \(s, s' \in S\) the source and target states, \(\alpha \in \actions\) the produced action, \(J' \subseteq J\) the holes involved in the transition, \(\beta_j \in \actions\) the actions of the holes, \(g \in \formulas\) the guard and \(\psi: V \to \terms\) the variables assignements.
 \end{defi}
-An open transition can have many unbound variable, actually an effective transition of the automaton is any well-formed substitution of the unbound variables of the transition minus the automaton variables.
-% This is used to constrain the infinite branching to be representable, making it possible to reason about.
+An open transition can have many unbound variables.
+Actually an effective transition of the automaton is any well-formed substitution of the unbound variables of the transition minus the automaton variables.
 
-The intuition of a semantic open automaton is a partially defined LTS with variables, guards on transitions and parametrised actions.
+The intuition of an open automaton is a partially defined LTS with variables, guards on transitions and parametrised actions.
 Initially the automaton is in the initial state with the initial valuation.
-In any state with any valuation, it can perform transitions which source state is the current state and which guard is valid in the current valuation if the holes emit the indicated action.
-By performing the transition the automaton emits the indicated action and updates its variables and state.
+In any state with any valuation, it can perform effective transitions which source state is the current state and which guard is satisfiable in the current valuation if the holes emit the indicated actions.
+An effective transition is a transition where every variable that is not an automaton variable is instanciated with a value.
+By performing the effective transition, the automaton emits the indicated action and updates its variables and state according to the target state and variables assignements.
 
-\begin{noti}[Bisimilarity, FH-bisimulation]
-The bisimilarity relation on open automata is noted \(\cong\) and the FH-bisimulation \cite{henrio:01055091} is noted \(\overset{FH}=\).
+\begin{noti}[FH-bisimulation]
+The FH-bisimulation \cite{henrio:01055091} is noted \(\cong\).
+
+The FH-bisimulation is currently the only equivalence relation on open automata.
 \end{noti}
-Note that FH-bisimilarity implies bisimilarity.
+To illustrate these definitions we consider two implementations (figure \ref{fig:enable}) of the LOTOS \cite{ISOLOTOS} operator enable in the open automata model.
+The enable operator runs  the left hand side agent until it chooses to finish, at which point it produces an action \(\delta\mpar{t}\) (with \(t\) some data) that is synchronised with the first action of the right hand side agent which must be \(\act{accept}\mpar{t}\) (here \(t\) is an input), then only the latter agent runs.
+The \(\act{accept}\) action is shortened as \(\act{acc}\) in the examples.
+During the synchronised action \Quentin{data can be exchanged}{I need to read a little bit more on that; is that a return code?}.
+\begin{exi}[Enable, state-oriented]
+Graphical convention for drawing automata are as follows.
+As standard automata, circles represent states and simple arrows represent transitions.
+The initial state is indicated by a double circle.
+States names are indicated inside the circles and transitions labels are drawn near their corresponding arrow.
+The open transitions do not indicate the source and target states since that is the role of the transitions arrows; only the emmited action is on the bottom side of open transitions.
+Initial valuations are indicated near a double lined arrow pointing to the initial state.
 
-To illustrate these definitions we consider  two implementations (figure \ref{fig:enable}) of the LOTOS \cite{ISOLOTOS} operator enable in the open automata model.
-The enable operator runs  the left hand side agent until it chooses to finish, at which point it produces an action \(\delta\) that is synchronised with the first action of the right hand side agent which must be \(\act{acc}\), then only the latter agent runs.
-During the synchronised action \Quentin{data can be exchanged}{I need to read a little bit more on that; is that a return code?}.
-
-\begin{exi}[Enable, state-oriented]
 \begin{figure}
@@
 \input{enable_var.tex}
-\caption{Enable operator implementation with open automata, on the left state oriented, on the right variable oriented}
+\caption{Enable operator implementation with open automata, on the left state oriented, on the right data oriented}
 \label{fig:enable}
 \end{figure}
-
-Graphical notations for showing automata are as follows.
-Automata are shown in the figure, the usual circle for states and simple arrows for transitions convention is used.
-The initial state is indicated by a double circle.
-States names are indicated inside the circles and transitions labels are drawn near their corresponding arrow.
-The open transitions do not indicate the source and target states since that is the role of the transitions arrows; only the action is on the bottom side of the open transition.
-Also in the example, transitions are specified using variables in place of actions.
-This is used to represent all the transitions created by a correct substitution of these variables, which cannot be drawn as there are often infinitely many.
-
-We can proceed to explain the left enable operator example.
-The automata on the left side is \(\OA{\mbrc{L, R}}{L}{\emptyset}{\mbrc{}}{\mbrc{l, r}}{T}\) where transitions in \(T\) are:
+The automaton on the left side of the figure is \(\OA{\mbrc{L, R}}{L}{\emptyset}{\mbrc{}}{\mbrc{l, r}}{T}\) where transitions in \(T\) are:
 \begin{align*}
-	\OT{L}{L}{x}{\mbrc{l \mapsto x}}{x \neq \delta}{\mbrc{}} &&
+	\OT{L}{L}{x}{\mbrc{l \mapsto x}}{\forall y, x \neq \delta\mpar{y}}{\mbrc{}} &&
 	\OT{L}{R}{\tau}{\mbrc{l \mapsto \delta\mpar{x}, r \mapsto \act{acc}\mpar{y}}}{x = y}{\mbrc{}} &&
@@
 \end{align*}
-Note that we could have expressed the transition in the middle with \(\mbrc{l \mapsto \delta\mpar{x}, r \mapsto \act{acc}\mpar{x}}\) which would have avoided many transitions with trivially false guards like the one where \(x \mapsto 1, y \mapsto 2\) which has the guard \(1 = 2\).
+Note that the transition in the middle could have been expressed as \(\mbrc{l \mapsto \delta\mpar{x}, r \mapsto \act{acc}\mpar{x}}\).
+It would have avoided many effective transitions with trivially false guards like the one where \(x \mapsto 1, y \mapsto 2\), which has the guard \(1 = 2\).
 
-This automaton is an implementation of the enable operator because it begins in the state \(L\) where it allows any transition from its hole \(l\) which is not \(\delta\) then the automaton synchronises its holes on the same data, effectively allowing a data exchange when it goes into state \(R\), and finally allows any transition from its hole \(r\).
+This automaton is an implementation of the enable operator because it begins in the state \(L\), where it allows any non \(\delta\) transition from its hole \(l\), then the automaton synchronises its holes on the same data, effectively allowing a data exchange when it goes into state \(R\), and finally allows any transition from its hole \(r\).
+The implementation of value passing in the open automata model doesn't distinguish input and output variables as in LOTOS.
+Both holes must emit their actions with valid data to perform the transition in the enable operator.
+If it is not possible the system is locked.
+
 We use the standard convention that uses \(\tau\) as a non-observable transition, never synchronised with other actions and passed unmodified.
@@
 However here \(\tau\) is not always allowed from the holes, for instance in the state \(L\) the hole \(r\) cannot emit it.
-These transition have been omitted for the sake of simplifying the first example of open automaton.
+These transitions have been omitted for the sake of simplifying the first example of open automata.
 \end{exi}
-
 Finally we can define some utilitary functions:
 \begin{defi}[Guard, Out-transition, Transition variables]
-Let \(V\) be the variable names of the considered automaton, \(T\) its transitions and \(s\) be one of its states.
-\(\fOT{s}\) are called the out-transitions of \(s\).
-\(\fIT{s'}\) are called the in-transitions of \(s'\).
+Let \(V\) be the variable names of the considered automaton, \(T\) its transitions and \(r\) one of its states.
+\(\fOT{r}\) are called the out-transitions of \(r\).
+\(\fIT{r}\) are called the in-transitions of \(r\).
+The local variables of a transition are all variables appearing in that transition except the global variables of the automaton.
 \begin{align*}
-	\fOT{t} & \defnotation \mset{\OTg \in T}{s = t} &
-	\fIT{t} & \defnotation \mset{\OTg \in T}{s' = t} \\
+	\fOT{r} & \defnotation \mset{\OTg \in T}{s = r} &
+	\fIT{r} & \defnotation \mset{\OTg \in T}{s' = r} \\
 \end{align*}
@@
 \end{defi}
+The goal of the extractor \(\fvars{t}\) when \(t\) is a transition is to get variables that are unique to that transition.
+Other variables like automaton variables are already known at this point so there is no use in getting them.
+Also the use of this extractor benefits from this exclusion: otherwise there would always be \(\setminus V\) following it to prevent variable shadowing.
 
 \begin{exi}[Enable, variable-oriented]
-The automata drawn on the right side of the figure is an alternative implementation of the enable operator which is FH-bisimilar to the previous one.
-The drawing introduces the double arrows which is used to denote the initial valuation.
-The automata drawn is \(\OA{\mbrc{\_}}{\_}{\mbrc{v}}{l^\mbrc{v}}{\mbrc{l, r}}{T}\) where transitions in \(T\) are:
+The automaton drawn on the right side of Figure \ref{fig:enable} is \(\OA{\mbrc{\_}}{\_}{\mbrc{v}}{l^\mbrc{v}}{\mbrc{l, r}}{T}\) where transitions in \(T\) are:
 \begin{align*}
@@
 \end{align*}
-Note that in this example \(r\) and \(l\) are a hole names and also closed terms: this is a naming conflict, we do not have \(J \subseteq \rterms\).
+It is an alternative implementation of the enable operator which is FH-bisimilar to the previous one, as proved in \marginpar{probably forte, check that}.
+Note that in this example \(r\) and \(l\) are a hole names and also closed terms: this is a naming conflict, though it is not ambiguous because \(J \cap \rterms = \emptyset\) always holds.
+The variables local to a transition are all the unbound variables in the expressions minus the automaton variables.
+For instance \(v\) is a variable of the automaton (used in the guard).
+It is not local to the transition.
+In a run, when taking effective transitions (without local variables), its value is not substituted with a closed term.
+For instance \nmm{\OT{\_}{\_}{\tau}{\mbrc{l \mapsto \tau}}{v = l \wedge \tau \neq \delta}{\mbrc{}}} is an effective transition generated from the second transition but not \nmm{\OT{\_}{\_}{\tau}{\mbrc{l \mapsto \tau}}{l = l \wedge \tau \neq \delta}{\mbrc{}}} (result of the forbidden substitution \(v \mapsto l\)).
 
-The variables of a transition are all the free variables in the expressions minus the automaton variables.
-For instance \(v\) is a variable name for the automaton which is used in the guard.
-It is not a transituon variable.
-When generating transition without free variables its value is not substituted with a closed term.
-For instance \nmm{\OT{\_}{\_}{\tau}{\mbrc{l \mapsto \tau}}{v = l \wedge \tau \neq \delta}{\mbrc{}}} is a transition generated by the second transition and is in \(T\) but not \nmm{\OT{\_}{\_}{\tau}{\mbrc{l \mapsto \tau}}{l = l \wedge \tau \neq \delta}{\mbrc{}}} (result of the forbidden substitution \(v \mapsto l\)).
+An imaginary run of this open automaton can be: The automaton in the hole \(l\) emits many actions, this synchronises with the only transition possible at that moment because \(v = l\).
+Then the automaton in hole \(l\) emits a \(\delta\mpar{t}\), this is synchonised with the action that sets \(v \gets r\) and the automata in hole \(r\) must emit a \(\act{acc}\mpar{t}\).
+Finally the automaton in the hole \(r\) emits any sequence of actions.
 
-An imaginary run of this open automaton can be the automaton in the hole \(l\) emits many actions, this synchronises with the only transition possible at that moment because \(v = l\).
-Then the automaton in hole \(l\) emits a \(\delta\mpar{t}\), this is synchonised with the action that sets \(v \gets r\) and the automata in hole \(r\) must emit a \(\act{acc}\mpar{t}\).
-Finally the automaton in the hole \(r\) emits any sequence of action.
-
-Another imaginary run can be the automaton in the hole \(l\) emits a sequence of action and the automaton in the hole \(r\) cannot emit a \(\act{acc}\mpar{t}\) so it never runs.
+Another imaginary run can be: The automaton in the hole \(l\) emits a sequence of non \(\delta\mpar{t}\) actions so the automaton in the hole \(r\) cannot emit a \(\act{acc}\mpar{t}\) and never runs.
 \end{exi}
 
-From this point open automata and open transitions will be called automata and transitions for simplicity.
+From this point open automata and open transitions can be called automata and transitions for simplicity. % NEED NORMALISATION, LEFT IN CASE OF OMISSION
 
-\section{Semantic and composition of Open Automata}\label{sec:semcompo}
-The interpretation of open automata is a partially specified automaton, where the partial specification comes from the holes.
-This specification can be completed by composing automata into holes so it is natural to take a look at the composition process.
-This was already defined on pNets in previous work \cite{henrio:01299562} but never completely formalised on open automata.
-The  definition of composition below is a direct translation of composition on pNets for open automata.
+\section{Composition of Open Automata}\label{sec:comp}
+Open automata are partially specified automata, part of that partiality comes from the holes.
+The interpretation of a hole is an interface with another open automaton, in which we can plug an open automaton with an operation called composition.
+The composition of open automata was already implicitely defined by the means of composition on pNets in previous work \cite{henrio:01299562} but never completely formalised on open automata.
+The definition of composition below is a direct translation of what happens with pNets composition without the need of introducing pNets.
 \begin{defi}[Composition of open automata]
@@
 	A_p\subst{A_c}{k} \defnotation & \OA{S_p \times S_c}{\mpar{s_{0p}, s_{0c}}}{V_p \uplus V_c}{\sigma_{0p} \uplus \sigma_{0c}}{J_c \uplus J_p \setminus \mbrc{k}}{T} \\
-	\text{With } T \defobject & \mset{\OT{\mpar{s_p, s_c}}{\mpar{s'_p, s'_c}}{\alpha_p}{\beta_j^{j \in J'_c \uplus J'_p \setminus \mbrc{k}}}{g_p \wedge g_c \wedge \alpha_c = \beta_k}{\psi_p \uplus \psi_c}}{\OTx{p}{}{}{p} \in T_p, \OTx{c}{}{}{c} \in T_c} \\
-	& \cup \mset{\OT{\mpar{s_p, s_c}}{\mpar{s'_p, s_c}}{\alpha_p}{\beta_j^{j \in J'_p}}{g_p}{\psi_p}}{\OTx{p}{}{}{p}, k \notin J', s_c \in S_c}
+	\text{with } T \defobject & \mset{\OT{\mpar{s_p, s_c}}{\mpar{s'_p, s'_c}}{\alpha_p}{\beta_j^{j \in J'_c \uplus J'_p \setminus \mbrc{k}}}{g_p \wedge g_c \wedge \alpha_c = \beta_k}{\psi_p \uplus \psi_c}}{\OTx{p}{}{}{p} \in T_p, \OTx{c}{}{}{c} \in T_c} \\
+	& \cup \mset{\OT{\mpar{s_p, s_c}}{\mpar{s'_p, s_c}}{\alpha_p}{\beta_j^{j \in J'_p}}{g_p}{\psi_p}}{\OTx{p}{}{}{p} \in T_p, k \notin J'_p, s_c \in S_c}
 \end{align*}
@@
 \end{defi}
-The actions emitted when \(A_c\) makes a transition is sychronised with the action of the hole \(k\) in transitions of \(A_p\) which have it as a hole actions (first transition set, \(\alpha_c = \beta_k\)).
-No transition of \(A_c\) is performed when a transition that do not refer to the hole \(k\) is performed in \(A_p\) (second transition set, \(k \notin J'\)).
-The composition may look like a handshake, with both automata running in parallel (product of states and joint variables) but it is actually not symmetric.
-\begin{exi}
-\begin{figure}
-\centering
-\input{Traffic_Lights_Spec.tex}
-\caption{The specification of a traffic light system}
-\label{fig:tls}
-\end{figure}
-\begin{figure}
-\centering
-\input{Traffic_Lights_Controller.tex}
-\vrule
-\input{Traffic_Lights_Register.tex}
-\caption{On the left: The controller agent; On the right: The counter agent}
-\label{fig:tlh}
-\end{figure}
-This example is derived and adapted from a traffic light controller in a collection of examples for pNets.
-It is supposed to be a single traffic light.
+The action emitted when \(A_c\) makes a transition is sychronised with the action of the hole \(k\) in transitions of \(A_p\) which have it as a hole action (first transition set, \(\alpha_c = \beta_k\)).
+The composition may look like a handshake, with both automata running in parallel (product of states and joint variables) however it is asymmetric because of the second transition set (\(k \notin J'_p\)):
+No transition of \(A_c\) is performed when a transition that do not refer to the hole \(k\) is performed in \(A_p\).
 
-Figure \ref{fig:tls} shows the light controller with some synchronisation logic.
-It  takes an unimplemented control circuit in the hole \(ctl\) which gives the timings and an also unimplemented counter in the hole \(cnt\) to count external \(\act{tick}\) actions.
-The three states are used to remember which colored light is on and this color can be retrieved by the environment by synchronising with the actions \(\act{onXxx}\) (Xxx is either Red, Yellow or Green) if it is not stored externally.
+An example of composition can be found in Appendix \ref{apx:composition}.
+Composition is a complex process that generates big automata with complex and potentially simplifiable transitions.
+However simplification is a hard problem that is not yet automatised on open automata, so from this point the guards and transitions will always be simplified by hand without further explaination.
 
-The color switches when the register and the control circuit agree that the time is over.
-The new time limit can be set by the control circuit and the exposed action to the exterior is a \(\tau\).
-
-The component we choose to compose in the holes are in Figure \ref{fig:tlh}.
-On the left is the controller agent which will be composed in the hole \(ctl\).
-Its role is to decide the duration before switching the lights.
-This implementation is simply a constant time for each color.
-
-On the right is the counter agent which will be composed in the hole \(cnt\).
-Its role is to get a target, then count ticks until that target is reached, then emit an action with the elapsed time and restart.
-This implementation does exactly that and forbids any extra tick.
-
-\begin{figure}
-\centering
-\input{Traffic_Lights_Full.tex}
-\caption{The full traffic lights system}
-\label{fig:tlf}
-\end{figure}
-The automaton on Figure \ref{fig:tlf} is bisimilar to the composition of the specification on Figure \ref{fig:tls} and the agents on Figure \ref{fig:tlh}.
-The result of the composition has 36 states (\(3 \times 2 \times 6\)) but only 6 are reachable from the initial configuration.
-The transitions obtained by composition were simplified to give the following (where \(n, n+1\) stands for numbers between 1 and 6 and Xxx is either Red, Yellow or Green):
-\begin{itemize}
-\item \nmm{\OT{XnS}{X(n+1)C}{\tau}{\mbrc{}}{\top}{\mbrc{t \gets k, c \gets 0}}} which is the composition of \nmm{\OT{X}{X}{\tau}{\mbrc{ctl \mapsto \theta\mpar{x}, cnt \mapsto \act{set}\mpar{x}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{S}{C}{\act{set}\mpar{x}}{\mbrc{}}{\top}{\mbrc{t \gets x, c \gets 0}}} from the counter and \nmm{\OT{n}{n+1}{\theta\mpar{k}}{\mbrc{}}{\top}{\mbrc{}}} from the controller.
-\item \nmm{\OT{XnC}{XnC}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} which is the composition of \nmm{\OT{X}{X}{\act{tick}}{\mbrc{cnt \mapsto \act{tick}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} from the counter.
-\item \nmm{\OT{YnC}{X(n+1)S}{\act{TurnXxx}}{\mbrc{}}{c = t}{\mbrc{}}} which is the composition of \nmm{\OT{Y}{X}{\act{TurnXxx}}{\mbrc{cnt \mapsto \act{over}\mpar{x}, ctl \mapsto \delta\mpar{x}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{C}{S}{\act{over}\mpar{c}}{\mbrc{}}{c = t}{\mbrc{}}} from the counter and \nmm{\OT{n}{n+1}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} from the controller.
-\end{itemize}
-
-To illustrate composition, simplification and value passing, the \(\tau\) transition from the state \(R\) will be examined.
-The transition in the specification is \nmm{\OT{R}{R}{\tau}{\mbrc{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}.
-The composition can produce 12 states containing the \(R\) state, these states are in \(\mbrc{R} \times \mdbrk{1; 6} \times \mbrc{S, C}\), however only \(R1S\) and \(R2C\) are reachable so we will only consider \(\tau\) transitions from these two.
-The holes \(cnt\) and \(ctl\) are both involved in the \(\tau\) transition and filled with automata so the composed automata must synchronise with a transition.
-
-In the state \(R2C\) the composition produces 2 transition by composition out of the \(\tau\) transition but both have a false guard; It is still interesting to look at one of them to show the product of composition without simplification.
-
-\nmm{\OT{R2C}{R3C}{\tau}{\mbrc{}}{\top \wedge \top \wedge c < t \wedge \act{set}\mpar{x} = \act{tick} \wedge \theta\mpar{x} = \delta\mpar{x_C}}{\mbrc{c \gets c + 1}}} is made with \nmm{\OT{2}{3}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} from the controller and \nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} from the counter.
-Obviously the equality of actions in the guard cannot be satisfied so the guard is false, it is equivalent to have no transition.
-We could go on to another transition but something worth explaining happened to build its guard.
-The first two \(\top\) come from the guards of the specification and the controller.
-\(c < t\) comes from the counter.
-The rest of the guard comes from the equality constraint between holes actions and automata actions.
-When composing this expression, we can see that the \(x\) variables from the specification, the controller and the counter are in conflict.
-To resolve the conflict the conflicted variables are renamed depending on where they come from.
-
-In the state \(R1S\) the composition produces 1 transition out of the \(\tau\) transition.
-The simplified transition is described before, yet examining the composition process can illustrate how value passing work.
-The obtained guard is \(\top \wedge \top \wedge \top \wedge \theta\mpar{x} = \theta\mpar{17} \wedge \act{set}\mpar{x} = \act{set}\mpar{x_R}\) and the obtained variable assignment is \(\mbrc{t \gets x_R, c \gets 0}\).
-We can see how value passing works in the equality constraints: the only possible value of \(x\) and \(x_R\) making the guard hold is \(17\), this value has been synchronised from the controller to \(x\) then to the second occurrence of \(x\) to the distinct \(x\) of the counter.
-Note that \nmm{\OT{S}{C}{\act{set}\mpar{t}}{\mbrc{}}{\top}{\mbrc{c \gets 0}}} wouldn't have worked as a transition for the controller because \(t\) is not a transition variable, its value is fixed before the transition and cannot be set outside of the variable update, hence the use of an auxiliary variable \(x\).
-
-From this point the guard and transition will always be simplified.
-\end{exi}
-
-\section{What is a refinement for Open Automata}\label{sec:proofelts}
+% TODO HERE: relecture
+\section{Properties of a refinement relation for Open Automata}\label{sec:proofelts}
 There are several properties that we may want from a refinement relation.
-Depending on these properties, several kinds of refinement may be used.
+Depending on these properties, different kinds of refinement can be used.
 For example if we are interested in producing the same sequence of actions we may want to use trace set inclusion as a refinement.
-Here the main properties that we want are related to composition and action refinement.
+Here the main properties that we want are related to composition and action refinement. % LATER: explain here or remove if not tackled
 Because of composition, a relation as strong as simulation refinement must be used as observed in the articles about FH-bisimulation \cite{henrio:01055091}.
@@
 \defitem \textbf{correct w.r.t.\@ composition} iff \(\forall a\, b, a\mbrk{b} \leq a\);
-\defitem \textbf{complete w.r.t.\@ composition} iff \(\forall a\, b, a \leq b \implies \exists c, a \overset{FH}= b\mbrk{c}\);
+\defitem \textbf{complete w.r.t.\@ composition} iff \(\forall a\, b, a \leq b \implies \exists c, a \cong b\mbrk{c}\);
 \defitem \textbf{context refining for composition} iff \(\forall a\, b\, c, a \leq b \implies a\mbrk{c} \leq b\mbrk{c}\);
@@
 \defitem \textbf{compatible with composition} iff \(\forall a\, b\, c\, d, a \leq b \wedge c \leq d \implies c\mbrk{a} \leq d\mbrk{b}\);
-\defitem \textbf{compatible with FH-bisimulation} iff \(\forall a\, b\, c, d, a \overset{FH}= b \wedge c \overset{FH}= d \wedge a \leq c \implies b \leq d\).
+\defitem \textbf{compatible with FH-bisimulation} iff \(\forall a\, b\, c, d, a \cong b \wedge c \cong d \wedge a \leq c \implies b \leq d\).
 \end{defi}
@@
 Correctness w.r.t.\@ composition is the fact that every composition is considered a refinement.
+This property is what we want to capture with a refinement relation for a structure with composition like the open automata.
 Completeness w.r.t.\@ composition is the fact that a refinement correspond to the left automaton being equivalent to some composition of the right automaton.
+This property is useful if we want to caracterise the kind of operations that can generate any refined automaton starting from the specification.
+We wont have it because setting more automaton variables in the initial configuration will be a refinement and it can't be expressed by composing.
+Yet a completeness with respect to some base of operation is still a strong and interesting property.
 Context refinement is the refinement being compatible with composition of the same automaton.
@@
 Compatibility with composition is the conjunction of the two latter (assuming the relation is a preorder).
+This property is also a must have on compositionnal structures to be of any use in proofs and for model checking.
 Finally compatibility with FH-bisimulation is the refinement not being able to distinguish two FH-bisimilar automata.
+Since FH-bisimulation is the pre-existing practical equivalence relation, we should not introduce an incompatible proof strategy.
 
@@
 In the weak refinement the relations have to forbid the introduction of livelocks (only a sequence of \(\tau\) possible) and respect \(\tau\)-stuttering \marginpar{cite many things arround here}.
+
+The non introduction of deadlocks/livelocks are important properties because deadlocks/livelocks can arise in unpredicable ways when parallelism is involved.
+The deadlocks/livelocks break the intended behaviour of a system and by preventing them we could hope that the refinement preserves some liveness properties.
 \Ludo{to add}{I believe we want more arguments on why we want some properties, at least deadlock and livelock related, perhaps also weak vs strong.
@@
 \begin{defi}[Relation under predicate]
-A relation under predicate between states of two automata \(\OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(\OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) is a function \(R: S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\).
+A relation under predicate between states of two automata \(\OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(\OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) is a function \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
 
@@
 For a relation \(\wrel{}{}{}\) which uses a relation under predicate to prove that two element are related \(\forall x \, x', x \wrel{}{}{} x' \iff \exists R, P\mpar{R}\), the fact that there is a valid witness \(R\) is noted \(\wrel{x}{x'}{R}\).
+% TODO REDO: objectif, introduire wrel
 \end{defi}
@@
 \begin{defi}[Simulation on open automata] % TODO: faire une définition standard
-A relation \(\leq\) is a simulation if for any two related automata \(\wrel{A_1}{A_2}{R}\) where \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\), \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and \(R: S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\), \(R\) satisfies both
+A relation \(\leq\) is a simulation if for any two related automata \(\wrel{A_1}{A_2}{R}\) where \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\), \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\), \(R\) satisfies both
 \defitem Initial states are related under initial valuations: \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\);
@@
 \end{defi}
+% TODO: rassurer le lecteur, il a bien lu, ce qu'il se passe sur les trous est contre-intuitif
 The last formula means that for every pair of related states under valuation of the automaton variables and every possible transitions (\(\vdash g_1\)) from the first automaton, there is a possible transition (\(\vdash g_2\)) such that the produced action matches (\(\alpha_1 = \alpha_2\)), the holes actions from same hole names (\(J'_1 \cap J'_2\)) match (\(\beta_{1j} = \beta_{2j}\)) and the target states are related after variable update.
@@
 \begin{defi}[Deadlock reduction, intuitive definition]
-A simulation \(\leq\) is deadlock reducing if in all the \(R: S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\) such that \(\wrel{A_1}{A_2}{R}\), there is one that also satisfies
+A simulation \(\leq\) is deadlock reducing if in all the \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) such that \(\wrel{A_1}{A_2}{R}\), there is one that also satisfies
 \begin{multline*}
@@
 \end{defi}
+% TODO: repasser a un implique
 This definition \Ludo{extends the requirements of a simulation}{je suis pas d accord avec cette affirmation, ou tout du moins c est pas evident} by requiring from the relation that on related states, either there is a pair of possible matching transition or there was no out-transition possible in the specification.
@@
 
-``Deadlock reduction" conflicts with ``composition completeness" by disallowing some unwanted cases where an automaton in a hole cannot produce any action that any out-transitions expects.
+``Deadlock reduction" conflicts with ``composition correctness" by disallowing some unwanted cases where an automaton in a hole cannot produce any action that any out-transitions expects.
 In particular filling a hole with the deadlock automaton (only one state without out-transitions) is not considered a refinement for a \Ludo{deadlock reducing simulation refinement}{define or use the name of the definition}.
@@
 \begin{defi}[Reachability]
-For any open automata \(A \defobject \OA{S}{s_0}{V}{\sigma_0}{J}{T}\), a reachability predicate \(\reach{A}: S \to \rformulae[V]\) is a predicate on states such that
+For any open automata \(A \defobject \OA{S}{s_0}{V}{\sigma_0}{J}{T}\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is a predicate on states such that
 \defitem \(\sigma_0 \vdash \reach{A}\mpar{s_0}\).
@@
 This effectively makes reachability account for all paths and potentially over-approximate the reachable configurations.
-However the exact reachability may not be reprensentable in the formulae, hence the need of potentially over-approximating.
+However the exact reachability may not be reprensentable in the formulas, hence the need of potentially over-approximating.
 
@@
 \begin{defi}[Non-locking composition, intuitive definition]
-
 The composition  \(A_p\subst{A_c}{k} = \OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(A_c \defobject \OA{S_c}{s_{0c}}{V_c}{\sigma_{0c}}{J_c}{T_c}\), \(A_p \defobject \OA{S_p}{s_{0p}}{V_p}{\sigma_{0p}}{J_p}{T_p}\) and \(k \in J_p\), is a non-locking composition if there is a reachability predicate such that from reachable configurations, either a transition is possible in \(A_p\subst{A_c}{k}\) or there were no possible transition in \(A_p\) to begin with
@@
 
-If the hole cannot register a \(\act{tick}\) at any time then there is a deadlock, which is the case with our counter.
+If the hole cannot handle a \(\act{tick}\) at any time then there is a deadlock, which is the case with our counter.
 The composition of this clock with the counter is given on the left of Figure \ref{fig:deadlock}.
@@
 We could have defined the non-locking composition so that this is considered as an intended deadlock, making the requirement symetric.
-However the the semantic of composition in a hole is assymetric and the considered specification -as in the deadlock reduction- is the parent automaton.
+However the the semantics of composition in a hole is assymetric and the considered specification -as in the deadlock reduction- is the parent automaton.
 A symetric version is presented in Section ???\marginpar{TODO LATER}, where we introduce a more symetric model of open automata.
@@
 \begin{defi}[Deadlock reduction, working definition]
-A simulation \(\leq\) is deadlock reducing if in all the \(R: S_1 \times S_2 \to \rformulae[V_1 \uplus V_2]\) such that \(\wrel{A_1}{A_2}{R}\), there is one that also satisfies
+A simulation \(\leq\) is deadlock reducing if in all the \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) such that \(\wrel{A_1}{A_2}{R}\), there is one that also satisfies
 \begin{multline*}
@@
 \end{lem}
-Proof of both lemma are given in appendix \ref{apx:lemeqd}.
-
-% TODO?: sufficient condition
+Proof of both lemma are given in Appendix \ref{apx:lemeqd}.
 
@@
 %\end{figure}
-An example of non-locking parallel substitution where no individual substitution is non-locking is given in Figure \ref{fig:pnls}.% TODO HERE
+% An example of non-locking parallel substitution where no individual substitution is non-locking is given in Figure \ref{fig:pnls}.% TODO HERE
 %\end{exi}
@@
 If \(J_1 = J_2\) then ``\(A_1\) is a hole-identical refinement of \(A_2\)", noted \(A_1 \leq_= A_2\), is defined as:
-\[ \exists R: \mpar{S_1 \times S_2} \to \rformulae[V_1 \uplus V_2], \sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}} \qwedge R \text{ hole-identical simulation of } A_1 \text{ in } A_2 \]
+\[ \exists R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2], \sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}} \qwedge R \text{ hole-identical simulation of } A_1 \text{ in } A_2 \]
 \end{defi}
@@
 If \(J_1 \subseteq J_2\) then ``\(A_1\) is a hole-subset refinement of \(A_2\)", noted \(A_1 \leq_\subseteq A_2\) is defined as:
-\[ \exists R: \mpar{S_1 \times S_2} \to \rformulae[V_1 \uplus V_2], \sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}} \wedge R \text{ hole-subset simulation of } A_1 \text{ in } A_2 \]
+\[ \exists R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2], \sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}} \wedge R \text{ hole-subset simulation of } A_1 \text{ in } A_2 \]
 \end{defi}
@@
 \begin{multline*}
-	\exists R: \mpar{S_1 \times S_2} \to \formulae, \quad \exists f: J_1 \setminus J_2 \to J_2 \setminus J_1, \\
+	\exists R: \mpar{S_1 \times S_2} \to \formulas, \quad \exists f: J_1 \setminus J_2 \to J_2 \setminus J_1, \\
 	\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}} \qwedge f\mpar{J_1 \setminus J_2} = J_2 \setminus J_1 \\
@@
 \begin{multline*}
-	\exists R: \mpar{S_1 \times S_2} \to \rformulae[V_1 \uplus V_2], \exists f: J_1 \setminus J_2 \to J_2 \setminus J_1, \\
+	\exists R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2], \exists f: J_1 \setminus J_2 \to J_2 \setminus J_1, \\
 	\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}} \wedge R \text{ f simulation of } A_1 \text{ in } A_2
@@
 
+\section{Future work}
+
 \section{Conclusion}
@@
 
+\section{Example of composition}\label{apx:composition}
+\begin{figure}[h]
+\centering
+\input{Traffic_Lights_Spec.tex}
+\caption{The specification of a traffic light system}
+\label{fig:tls}
+\end{figure}
+\begin{figure}
+\centering
+\input{Traffic_Lights_Controller.tex}
+\vrule
+\input{Traffic_Lights_Register.tex}
+\caption{On the left: An example of controller agent; On the right: An example of counter agent}
+\label{fig:tlh}
+\end{figure}
+This example is derived and adapted from a traffic light controller in a collection of examples for pNets.
+It is supposed to be a single traffic light.
+
+Figure \ref{fig:tls} shows the light controller with some synchronisation logic.
+It  takes an unimplemented control circuit in the hole \(ctl\) which gives the timings and an also unimplemented counter in the hole \(cnt\) to count external \(\act{tick}\) actions.
+The three states are used to remember which colored light is on and this color can be retrieved by the environment by synchronising with the actions \(\act{onXxx}\) (Xxx is either Red, Yellow or Green) if it is not stored externally.
+
+The color switches when the counter and the control circuit agree that the time is over.
+The new time limit can be set by the control circuit and the exposed action to the exterior is a \(\tau\).
+
+The components we choose to compose in the holes are in Figure \ref{fig:tlh}.
+On the left there is the controller agent which will be composed in the hole \(ctl\).
+Its role is to decide the duration before switching the lights.
+This implementation is simply a constant time for each color; we could imagine using a more fancy controller which decides of the time depending on the traffic of each lane.
+
+On the right is the counter agent which will be composed in the hole \(cnt\).
+Its role is to get a target, then count ticks until that target is reached, then emit an action with the elapsed time and restart.
+This implementation does exactly that and forbids any extra tick.
+
+\begin{figure}
+\centering
+\input{Traffic_Lights_Full.tex}
+\caption{The full traffic lights system}
+\label{fig:tlf}
+\end{figure}
+The automaton on Figure \ref{fig:tlf} is a simplification of the composition of the specification on Figure \ref{fig:tls} and the agents on Figure \ref{fig:tlh}.
+The simplification was hand made because it is a hard problem as explained at the end of Section \ref{sec:comp}.
+It consisted in removing unreachable states, reducing the size of the guard and reducing the amount of variables.
+Otherwise the figure would have 36 states (\(3 \times 2 \times 6\)) but only 6 reachable from the initial configuration.
+The simplified transitions are the following (where \(n, n+1\) stands for numbers between 1 and 6, Xxx is either Red, Yellow or Green and \(\mpar{Y, X}\) is accordingly \(\mpar{Y, R}\), \(\mpar{R, G}\) or \(\mpar{G, Y}\)):
+\begin{itemize}
+\item \nmm{\OT{XnS}{X(n+1)C}{\tau}{\mbrc{}}{\top}{\mbrc{t \gets k, c \gets 0}}} which is the composition of \nmm{\OT{X}{X}{\tau}{\mbrc{ctl \mapsto \theta\mpar{x}, cnt \mapsto \act{set}\mpar{x}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{S}{C}{\act{set}\mpar{x}}{\mbrc{}}{\top}{\mbrc{t \gets x, c \gets 0}}} from the counter and \nmm{\OT{n}{n+1}{\theta\mpar{k}}{\mbrc{}}{\top}{\mbrc{}}} from the controller.
+\item \nmm{\OT{XnC}{XnC}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} which is the composition of \nmm{\OT{X}{X}{\act{tick}}{\mbrc{cnt \mapsto \act{tick}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} from the counter.
+\item \nmm{\OT{YnC}{X(n+1)S}{\act{TurnXxx}}{\mbrc{}}{c = t}{\mbrc{}}} which is the composition of \nmm{\OT{Y}{X}{\act{TurnXxx}}{\mbrc{cnt \mapsto \act{over}\mpar{x}, ctl \mapsto \delta\mpar{x}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{C}{S}{\act{over}\mpar{c}}{\mbrc{}}{c = t}{\mbrc{}}} from the counter and \nmm{\OT{n}{n+1}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} from the controller.
+\end{itemize}
+
+To illustrate composition, hand made simplifications and value passing, the \(\tau\) transition from the state \(R\) will be examined.
+The transition in the specification is \nmm{\OT{R}{R}{\tau}{\mbrc{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}.
+The composition can produce 12 states containing the \(R\) state, these states are in \(\mbrc{R} \times \mdbrk{1; 6} \times \mbrc{S, C}\), however only \(R1S\) and \(R2C\) are reachable so we will only consider \(\tau\) transitions from these two.
+The holes \(cnt\) and \(ctl\) are both involved in the \(\tau\) transition and filled with automata so the composed automata must synchronise with a transition.
+
+In the state \(R2C\) the composition produces 2 transitions by composition out of the \(\tau\) transition but both have a false guard; It is still interesting to look at one of them to show the product of composition without simplification.
+
+\nmm{\OT{R2C}{R3C}{\tau}{\mbrc{}}{\top \wedge \top \wedge c < t \wedge \act{set}\mpar{x} = \act{tick} \wedge \theta\mpar{x} = \delta\mpar{x_C}}{\mbrc{c \gets c + 1}}} is made with \nmm{\OT{2}{3}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} from the controller and \nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} from the counter.
+Obviously the equality of actions in the guard cannot be satisfied so the guard is false, it is equivalent to have no transition.
+We could go on to another transition but something worth explaining happened to build its guard.
+The first two \(\top\) come from the guards of the specification and the controller.
+\(c < t\) comes from the counter.
+The rest of the guard comes from the equality constraint between holes actions and automata actions.
+When composing this expression, we can see that the \(x\) variables from the specification, the controller and the counter are in conflict.
+To resolve the conflict, the conflicted variables were renamed depending on where they come from.
+
+In the state \(R1S\) the composition produces 1 transition out of the \(\tau\) transition.
+The simplified transition follows the first pattern in the transitions described before.
+Examining the composition process can illustrate how value passing work.
+The obtained guard is \(\top \wedge \top \wedge \top \wedge \theta\mpar{x} = \theta\mpar{17} \wedge \act{set}\mpar{x} = \act{set}\mpar{x_R}\) and the obtained variable assignment is \(\mbrc{t \gets x_R, c \gets 0}\).
+We can see how value passing works in the equality constraints: the only possible value of \(x\) and \(x_R\) making the guard hold is \(17\), this value has been synchronised from the controller to \(x\) then to the second occurrence of \(x\) to the distinct \(x\) of the counter.
+Note that \nmm{\OT{S}{C}{\act{set}\mpar{t}}{\mbrc{}}{\top}{\mbrc{c \gets 0}}} wouldn't have worked as a transition for the controller because \(t\) is not a transition variable, its value is fixed before the transition and cannot be set outside of the variable update, hence the use of an auxiliary variable \(x\).
+
 \section{Proof of equivalent definitions}\label{apx:lemeqd}
-\begin{proof}[Proof of lemma 1]
+
+\subsection{Proof of lemma 1}
+\begin{proof}
 Let \(R\), \(A_1 \defobject \OA{S_1}{s_{01}}{V_1}{\sigma_{01}}{J_1}{T_1}\), \(A_2 \defobject \OA{S_2}{s_{02}}{V_2}{\sigma_{02}}{J_2}{T_2}\) be such that:
@@
 \end{multline}
-\item[\bf(\ref{eq:drWD})\(\implies\)(\ref{eq:drID}):]
+\item[\(\eqref{eq:drWD}\Rightarrow\eqref{eq:drID}\):]
 	Let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \(\sigma: V_1 \uplus V_2 \to \values\) be such that:
@@
 	The witnesses for \goal{1} are \(t'_2\) and \(t_1\), and the rest is proved with a combination of \hyp{target} and \hyp{3'}.
-\item[\bf(\ref{eq:drWD})\(\impliedby\)(\ref{eq:drID}):]
+\item[\(\eqref{eq:drWD}\Leftarrow\eqref{eq:drID}\):]
 	Let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \(\sigma: V_1 \uplus V_2 \uplus \bigcup_{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values\).
 	We want to prove:
-	\[ \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{1} \]
-	We can admit the left part of the implication in which we decompose the big disjunction to get \(t_2 \in \fOT{s_2}\) and:
-	\begin{align*}
-		\sigma \vdash R\mpar{s_1, s_2} & \text{ \hyp{1}} &
-		\sigma \vdash \fguard{t_2} & \text{ \hyp{2}}
-	\end{align*}
+	\[ \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{2} \]
+	We can admit the left part of the implication in which we decompose the big disjunction to get \(t_2 \in \fOT{s_2}\) and:\\
+	\begin{minipage}{0.5\textwidth}\[ \sigma \vdash R\mpar{s_1, s_2} \hyp{4} \]\end{minipage}
+	\begin{minipage}{0.5\textwidth}\[ \sigma \vdash \fguard{t_2} \hyp{5} \]\end{minipage}
 	We are left to prove:
-	\[ \sigma \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{1'} \]
-	To do that we use (\ref{eq:drID}) with the current value of \(\mpar{s_1, s_2}\) and \(\sigma\), and prove the premisse of the implication with \hyp{1} to get:
+	\[ \sigma \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{2'} \]
+	To do that we use (\ref{eq:drID}) with the current value of \(\mpar{s_1, s_2}\) and \(\sigma\), and prove the premisse of the implication with \hyp{4} to get:
 	\begin{multline}
@@
 		\end{array}} \\
-		\vee \forall t_2 \in \fOT{s_2}, \forall \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \nvdash \fguard{t_2} \hyp{3}
+		\vee \forall t_2 \in \fOT{s_2}, \forall \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \nvdash \fguard{t_2} \hyp{6}
 	\end{multline}
-	There are two cases in this disjunction, the second is in contradiction with \hyp{2} and the first gives \(t_1\), \(t'_2\) and \(\nu\) such that (only the interesting part of the conjunction has been extracted):
-	\[ \sigma \uplus \nu \vdash \fguard{t_1} \hyp{4} \]
-	Which proves \goal{1'} with the values of \(\nu\) for the variables of \(\fguard{t_1}\) and dummy values for the other guards.
+	There are two cases in this disjunction, the second is in contradiction with \hyp{5} and the first gives \(t_1\), \(t'_2\) and \(\nu\) such that (only the interesting part of the conjunction has been extracted):
+	\[ \sigma \uplus \nu \vdash \fguard{t_1} \hyp{7} \]
+	Which proves \goal{2'} with the values of \(\nu\) for the variables of \(\fguard{t_1}\) and dummy values for the other guards.
 \end{proof}
 
-\begin{proof}[Proof of lemma 2]
+\subsection{Proof of lemma 2}
+\begin{proof}
 \[ \forall s \in S, \forall \sigma: V \uplus \bigcup_\subbox{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fvars{t_p} \to \values, \sigma \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \tag{WD}\label{eq:nlcWD} \]
@@
 \end{multline*}
-\item[\bf(\ref{eq:nlcWD})\(\implies\)(\ref{eq:nlcID}):]
+\item[\(\eqref{eq:nlcWD}\Rightarrow\eqref{eq:nlcID}\):]
 	Let \(s \in S\) and \(\sigma \in V \to \values\) be such that:
@@
 	Which is proved on \(t\) with valuation \(\mu\) by \hyp{3'}.
-\item[\bf(\ref{eq:nlcWD})\(\impliedby\)(\ref{eq:nlcID}):]
+\item[\(\eqref{eq:nlcWD}\Leftarrow\eqref{eq:nlcID}\):]
 	Let \(s \in S\), \(\sigma \in V \uplus \bigcup_{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fvars{t_p} \to \values\).
@@
 	\[ \sigma \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \goal{1} \]
-	We can admit the left part of the implication in which we decompose the big disjunction to get \(t_p\) and:
-	\begin{align*}
-		\sigma \vdash \reach{A}\mpar{s} & \text{ \hyp{1}} &
-		\sigma \vdash \fguard{t_p} & \text{ \hyp{2}}
-	\end{align*}
+	We can admit the left part of the implication in which we decompose the big disjunction to get \(t_p\) and:\\
+	\begin{minipage}{0.5\textwidth}\[ \sigma \vdash \reach{A}\mpar{s} \hyp{4} \]\end{minipage}
+	\begin{minipage}{0.5\textwidth}\[ \sigma \vdash \fguard{t_p} \hyp{5} \]\end{minipage}
 	We are left to prove:
 	\[ \sigma \vdash \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \goal{1'} \]
-	To do that we use (\ref{eq:nlcID}) with the current value of \(s\) and \(\sigma\), and prove the premisse of the implication with \hyp{1} to get:
+	To do that we use (\ref{eq:nlcID}) with the current value of \(s\) and \(\sigma\), and prove the premisse of the implication with \hyp{4} to get:
 	\begin{multline}
 		\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t} \\
-		\vee \forall t_p \in \fOT{\pi_{S_p}\mpar{s}}, \forall \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \nvdash \fguard{t_p} \hyp{3}
+		\vee \forall t_p \in \fOT{\pi_{S_p}\mpar{s}}, \forall \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \nvdash \fguard{t_p} \hyp{6}
 	\end{multline}
-	There are two cases in this disjunction, the second is in contradiction with \hyp{2} and the first gives \(t\) and \(\nu\) such that:
-	\[ \sigma \uplus \nu \vdash \fguard{t} \hyp{4} \]
+	There are two cases in this disjunction, the second is in contradiction with \hyp{5} and the first gives \(t\) and \(\nu\) such that:
+	\[ \sigma \uplus \nu \vdash \fguard{t} \hyp{7} \]
 	Which proves \goal{1'} with the values of \(\nu\) for the variables of \(\fguard{t}\) and dummy values for the other guards.

### 2021-05-17 2021-Refinement/report.tex
Section 5 cleaning begun

@@
 
-% TODO HERE: relecture
 \section{Properties of a refinement relation for Open Automata}\label{sec:proofelts}
-There are several properties that we may want from a refinement relation.
+There are several properties we may want from a refinement relation.
 Depending on these properties, different kinds of refinement can be used.
-For example if we are interested in producing the same sequence of actions we may want to use trace set inclusion as a refinement.
-Here the main properties that we want are related to composition and action refinement. % LATER: explain here or remove if not tackled
-Because of composition, a relation as strong as simulation refinement must be used as observed in the articles about FH-bisimulation \cite{henrio:01055091}.
+For example if we are interested in producing the same sequences of actions as another automaton we may want to use trace set inclusion as a refinement.
+Here the main expected properties are related to composition and action refinement. % LATER: explain here or remove if not tackled
+Because of composition, a relation as strong as simulation must be used as observed in the articles about FH-bisimulation \cite{henrio:01055091}.
+Informally, a simulation relation states that an automaton states and transitions can be simulated by another automaton.
 
@@
 
-The important properties we will consider here are:
+The important properties we consider are:
 \begin{defi} A relation \(\leq\) is
@@
 Reflexivity, transitivity and preorder are classical properties on relations.
-Correctness w.r.t.\@ composition is the fact that every composition is considered a refinement.
-This property is what we want to capture with a refinement relation for a structure with composition like the open automata.
-Completeness w.r.t.\@ composition is the fact that a refinement correspond to the left automaton being equivalent to some composition of the right automaton.
+Correctness w.r.t.\@ composition means that every composition is considered a refinement.
+This property captures the expectated behaviour of a refinement relation on a compositionnal structure like the open automata.
+Completeness w.r.t.\@ composition means that a refinement correspond to the left automaton being equivalent to some composition of the right automaton.
 This property is useful if we want to caracterise the kind of operations that can generate any refined automaton starting from the specification.
-We wont have it because setting more automaton variables in the initial configuration will be a refinement and it can't be expressed by composing.
-Yet a completeness with respect to some base of operation is still a strong and interesting property.
+We won't have it because setting more automaton variables in the initial configuration will be a refinement and it can't be expressed with composition.
+Yet a completeness with respect to some base of operations is still a strong and interesting property.
 Context refinement is the refinement being compatible with composition of the same automaton.
@@
 Compatibility with composition is the conjunction of the two latter (assuming the relation is a preorder).
-This property is also a must have on compositionnal structures to be of any use in proofs and for model checking.
+This property is a must have on compositionnal structures to be of any use in verification, proofs and for model checking.
 Finally compatibility with FH-bisimulation is the refinement not being able to distinguish two FH-bisimilar automata.
-Since FH-bisimulation is the pre-existing practical equivalence relation, we should not introduce an incompatible proof strategy.
+Since FH-bisimulation is the pre-existing equivalence relation, we should not introduce an incompatible proof strategy.
 
-The relations will have to be at least preorders, simulations and prevent the introduction of deadlocks to be called refinement simulation.
+The non introduction of deadlocks is also an important property.
 Deadlocks are states and valuations that are reachable in a run and from which no further transition is possible.
-On top of that weak refinement are refinement where some actions, typically one named \(\tau\), are considered not observable and can occur in the implementation while not having to be matched in the specification.
-In the weak refinement the relations have to forbid the introduction of livelocks (only a sequence of \(\tau\) possible) and respect \(\tau\)-stuttering \marginpar{cite many things arround here}.
+They can arise unpredictably when parallelism is involved (which is the case in our composition) and they break the intended behaviour of a system.
+By preventing them we could hope that the refinement preserves some liveness properties.
+While being preorder is simple to express for a relation, not introducing new deadlocks and being a simulation are properties about the states of the related automata.
+Therefore they are more complex to express.
+Thus the need of preliminary concepts before defining them.
 
-The non introduction of deadlocks/livelocks are important properties because deadlocks/livelocks can arise in unpredicable ways when parallelism is involved.
-The deadlocks/livelocks break the intended behaviour of a system and by preventing them we could hope that the refinement preserves some liveness properties.
-\Ludo{to add}{I believe we want more arguments on why we want some properties, at least deadlock and livelock related, perhaps also weak vs strong.
-How did you decide of the list of useful properties / when ais such or such property useful?}
-
-While being preorder is simple to express for a relation, being a simulation, do not introduce new deadlocks/livelocks and \(\tau\)-stuttering are properties about the states of the related automata, therefore they are more complex to express.
-We will need a preliminary concept before defining them.
+% TODO HERE: relecture
 \begin{defi}[Relation under predicate]
@@
 
+The relations will have to be at least preorders, simulations and prevent the introduction of deadlocks to be called refinement simulation.
 With all these properties we can now look at some concrete refinemet relations.
 
+% TODO: re-ecriture
 \section{Refinement relations in restricted cases}\label{sec:prelref}

### 2021-05-19 2021-Refinement/report.tex
Fixed between definitions 8 and 13 (both included)

@@
 \usepackage[colorlinks]{hyperref}
-% \usepackage{xcolor}
 \AtBeginDocument{\renewcommand\setminus{\smallsetminus}}
@@
 
+% TODO HERE: relecture
 \section{Properties of a refinement relation for Open Automata}\label{sec:proofelts}
@@
 Because of composition, a relation as strong as simulation must be used as observed in the articles about FH-bisimulation \cite{henrio:01055091}.
-Informally, a simulation relation states that an automaton states and transitions can be simulated by another automaton.
 
-% LATER
-% Other kind of refinement relation that \Quentin{I may explore}{This is a note for possible path, some may be explored, some may not.} are control refinement/hole refinement\footnote{No good formulation atm, the idea is that \(a \leq b \defnotation sth \wedge J_a \setminus J_b \leq_{ctrl} J_b \setminus J_a\), sth is probably a clause to ensure that they behave the same without holes involved.}, (meet semi)lattice refinement\footnote{meet = handshake, \(a \leq b \defnotation a = a || b\) with sync holes, I think this will be equivalent to hole-identical sim, (join=non-det choice?)}, weak-simulation refinement\footnote{Weak variation for each interesting simulation refinement}, composition-correct refinement\footnote{Basically a stricter variant of simulation-refinement where simulation has to take place the other way for some transitions (no different holes?) in order to be correct wrt composition}.
+Informally, a simulation relation relating two automata means that one automaton states and transitions can be simulated by the other automaton.
+Simulations are defined by relating states of automata.
+Two classical automata are called in simulation if there is a simulation relating their states.
 
-The important properties we consider are:
-\begin{defi} A relation \(\leq\) is
+Note that here there are two relations:
+The first is between states of two specific automata (\(R \subseteq S_1 \times S_2\)), the second is between automatas (\(A_1 \leq A_2\)).
+Generally the second is implicit because its definition is always \(\exists R \subseteq S_1 \times S_2, P\mpar{R}\) with \(P\) a property, and only talking about \(R\) and \(P\) is sufficient.
+However later on in this article we will define more complex relations on automata so we clarify the distinction now.
+A relation of second kind will be called ``relation on automata" whereas a relation of the first kind could be called ``relation on states" though valuations also play the same role as states.
+In the work on FH-bisimulation\marginpar{re-cite FH-bisim as near as the previous citation?} such a relation \(R\) was defined as triples in \(S_1 \times S_2 \times \formulas\) where for \(\mpar{s_1, s_2} \in S_1 \times S_2\) there is a unique \(f \in \formulas\) such that \(\mpar{s_1, s_2, f} \in R\).
+This is classically the definition of a function from \(S_1 \times S_2\) to \(\formulas\) so we will define it as such.
+\begin{defi}[Relation under predicate]
+A relation under predicate between states of two automata \(\OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(\OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) is a function \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
+
+Two states \(s_1 \in S_1, s_2 \in S_2\) with their respective valuations \(\sigma_1: V_1 \to \values, \sigma_2: V_2 \to \values\) are related iff \(\sigma_1 \uplus \sigma_2 \vdash R\mpar{s_1, s_2}\).
+\end{defi}
+For a relation on automata \(\wrel{}{}{}\) which uses a relation under predicate to state that two element are related \(\forall x \, x', \wrel{x}{x'}{} \iff \exists R, P\mpar{R}\), there is no unicity on \(R\).
+To specify which witness is used in \(\wrel{x}{x'}{}\), we note \(\wrel{x}{x'}{R}\) where \(R\) is that witness.
+
+The important properties we consider for the relation on automata are:
+\begin{defi} A relation on open automata \(\leq\) is
 \defitem \textbf{reflexive} iff \(\forall a, a \leq a\);
@@
 This property is useful if we want to caracterise the kind of operations that can generate any refined automaton starting from the specification.
-We won't have it because setting more automaton variables in the initial configuration will be a refinement and it can't be expressed with composition.
-Yet a completeness with respect to some base of operations is still a strong and interesting property.
+We won't have it because extending the domain of the initial valuation will be a refinement which can't be expressed with composition.
+Yet a ``completeness w.r.t.\@ some set of operations" is still a strong and interesting property.
 Context refinement is the refinement being compatible with composition of the same automaton.
@@
 
-The non introduction of deadlocks is also an important property.
-Deadlocks are states and valuations that are reachable in a run and from which no further transition is possible.
-They can arise unpredictably when parallelism is involved (which is the case in our composition) and they break the intended behaviour of a system.
-By preventing them we could hope that the refinement preserves some liveness properties.
-While being preorder is simple to express for a relation, not introducing new deadlocks and being a simulation are properties about the states of the related automata.
-Therefore they are more complex to express.
-Thus the need of preliminary concepts before defining them.
-
-% TODO HERE: relecture
-\begin{defi}[Relation under predicate]
-A relation under predicate between states of two automata \(\OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(\OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) is a function \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
-
-Two states \(s_1 \in S_1, s_2 \in S_2\) with their respective valuations \(\sigma_1: V_1 \to \values, \sigma_2: V_2 \to \values\) are related iff \(\sigma_1 \uplus \sigma_2 \vdash R\mpar{s_1, s_2}\).
-For a relation \(\wrel{}{}{}\) which uses a relation under predicate to prove that two element are related \(\forall x \, x', x \wrel{}{}{} x' \iff \exists R, P\mpar{R}\), the fact that there is a valid witness \(R\) is noted \(\wrel{x}{x'}{R}\).
-% TODO REDO: objectif, introduire wrel
-\end{defi}
-Now the properties about states of automata can be adapted to open automata.
-\begin{defi}[Simulation on open automata] % TODO: faire une définition standard
-A relation \(\leq\) is a simulation if for any two related automata \(\wrel{A_1}{A_2}{R}\) where \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\), \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\), \(R\) satisfies both
+The important properties we consider for the relation on states are being a simulation and the reduction of deadlocks as defined in the following definitions.
+\begin{defi}[Pre-simulation on open automata] % TODO: Is the definition satifying now?
+For two automata \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), a relation under predicate \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a pre-simulation if it satisfies both
 \defitem Initial states are related under initial valuations: \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\);
-\defitem From related states, all out-transitions from \(A_1\) can be simulated in \(A_2\) and their target states are \Ludo{related}{I am a bit surprised that $J_1$ and $J_2$ are unrelated and we only need to take only the intersection TBD}:
-\begin{multline*} % Mettre des sets de noms en commun qu'on veut effectivement mapper pour la transitivité
+\defitem From related states, all out-transitions from \(A_1\) can be simulated in \(A_2\) and their target states are related:
+\begin{multline*}
 	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \forall \sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values, \\
@@
 \end{defi}
-% TODO: rassurer le lecteur, il a bien lu, ce qu'il se passe sur les trous est contre-intuitif
 The last formula means that for every pair of related states under valuation of the automaton variables and every possible transitions (\(\vdash g_1\)) from the first automaton, there is a possible transition (\(\vdash g_2\)) such that the produced action matches (\(\alpha_1 = \alpha_2\)), the holes actions from same hole names (\(J'_1 \cap J'_2\)) match (\(\beta_{1j} = \beta_{2j}\)) and the target states are related after variable update.
-This is a natural extension of the notion of simulation on LTS, which is the same definition without variables and holes and guards.
-It will serve as a watchdog for any relation that will be defined with ``simulation" in its name, except weak-simulation where the transition from the first automaton that produce \(\tau\) actions are excluded.
+Apart from holes, this is a natural extension of the notion of simulation on LTS, which is the same definition without variables and holes and guards.
+The treatment of holes in the FH-bisimulation is that holes with the same name will receive the same open automata when composed and the resulting open automata will still be equivalent.
+Here we assume that one of the related open automata can be obtained by composing an open automaton in a hole, open automaton which can have holes itself.
+This implies that there is no relation between their holes (\(J \setminus \mset{k_i}{i \in \mdbrk{1; n}} \bigcup_{i \in \mdbrk{1; n}} J_i\) is neither subset nor superset of \(J_p\)).
+Yet we still assume that in holes with the same name, the same open automaton will be composed.
+Hence only the holes in common have to match their actions.
+However it is not sufficient to imply properties on the relation on automatons like being a preorder.
+It is only a necessary condition for any relation that will be defined with ``simulation" in its name.
 
-\begin{defi}[Deadlock reduction, intuitive definition]
-A simulation \(\leq\) is deadlock reducing if in all the \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) such that \(\wrel{A_1}{A_2}{R}\), there is one that also satisfies
+Deadlocks are states and valuations that are reachable in a run and from which no further transition is possible.
+They can arise unpredictably when parallelism is involved (which is the case in our composition) and they break the intended behaviour of a system.
+By preventing them we could hope that the refinement preserves some liveness properties.
+\begin{defi}[Deadlock reduction, intuitive definition] % TODO HERE: repasser a un implique
+A relation under predicate \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if:
+\defitem It is a pre-simulation;
+\defitem If from related states, there is a possible transition in the specification, then there is a pair of matching transition:
 \begin{multline*}
 	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \to \values, \mpar{\sigma \vdash R\mpar{s_1, s_2}} \implies \\
-	\mpar{\everymath{\displaystyle}\begin{array}{c}
-		\bigsymb{\exists} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_1} \uplus \fvars{t_2} \to \values, \\
+	\mpar{\exists t_2 \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \vdash \fguard{t_2}} \implies \\
+	\bigsymb{\exists} \mpar{t_1, t_2} \defobject \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2}, \exists \nu: \fvars{t_1} \uplus \fvars{t_2} \to \values, \\
 	\sigma \uplus \nu \vdash g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
-	\end{array}} \\
-	\vee \forall t_2 \in \fOT{s_2}, \forall \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \nvdash \fguard{t_2}
 \end{multline*}
 \end{defi}
-% TODO: repasser a un implique
-This definition \Ludo{extends the requirements of a simulation}{je suis pas d accord avec cette affirmation, ou tout du moins c est pas evident} by requiring from the relation that on related states, either there is a pair of possible matching transition or there was no out-transition possible in the specification.
-This requirement effectively prevents the presence of deadlock state in the first automaton if there is a related non-deadlock state in the second.
+This requirement effectively prevents the presence of deadlock state in the first automaton if there is a related non-deadlock state in the second by contraposition.
+On top of that the transition preventing the deadlock has to be an existing transition in the specification.
+This is because a valid transition unmatched in the specification is not a deadlock, yet we do not want it.
+The direct formulation of the property would also have required the unintuitive quantification on a possibly empty set of transition to state that they are impossible.
+The two previous reasons motivated the formulation in contraposed form.
 
-% LATER: livelock and tau-stuttering
-% \item[Livelock reduction:] If \(a \leq b\) then \(a\) does not introduces new livelocks, noted \(a \preceq b\) in the following; % Find a better place to introduce a better definition of livelock reduction.
-% \defitem \textbf{\(\tau\)-stuttering} iff .
-
-% LATER: modify or remove it
-% On the other hand there is a property that we considered for some time, that may arise when designing a refinement relation and that is interesting but actually unwanted:
-% \begin{description}
-% \item[Daisy equivalence:] \(a\mbrk{D} \leq a \wedge a \leq a\mbrk{D}\), where \(D\) is the single state automaton that can produce any action.
-% \end{description}
-% This property state that composing a hole with an automaton which can do anything is not a strict refinement.
-% While it might seem to be a natural property because this automaton is the closest to the meaning of a hole in term of automaton, there is actually a difference between the two.
-% Daisy equivalence allows to refine by filling a hole but also by going the other way, that is creating a hole name and putting its hole action to any transition (and possibly keeping any of the unmodified transitions).
-% The unwanted behaviour arise for instance when two independant holes are filled, then a hole is created and its actions are put where the two other actions were.
-% This effectively merges independant holes, or equivalently allows to consider that an automaton can be plug simultaneously into several holes which is not part of the composition semantics.
-% \begin{exi}
-% \end{exi}
-
-``Deadlock reduction" conflicts with ``composition correctness" by disallowing some unwanted cases where an automaton in a hole cannot produce any action that any out-transitions expects.
-In particular filling a hole with the deadlock automaton (only one state without out-transitions) is not considered a refinement for a \Ludo{deadlock reducing simulation refinement}{define or use the name of the definition}.
-% Unfold a little bit and remove refinement
-A way to solve this \Ludo{issue}{why is this an issue?
-can be solved by stating which properties are desirable for which reason above} is to characterise a composition that do not introduce deadlocks, which will be used instead of the composition introduced earlier.
-% Issue référence le conflit mais ce n'est pas clair, clarifie ça, replace issue with conflict
+In all these properties, ``Deadlock reduction" conflicts with ``composition correctness" by disallowing some unwanted cases where an automaton in a hole cannot produce any action that any out-transition expects.
+In particular filling a hole with the deadlock automaton (only one state without out-transitions) is not considered a refinement for a deadlock reducing relation.
+A way to solve this conflict is to characterise a composition that do not introduce deadlocks, which will be used instead of the composition introduced earlier.
 \begin{defi}[Reachability]
@@
 
-Another way of understanding this predicate is that it is a fixpoint of the union of valuations that contains the initial valuation:
+Another way of understanding this predicate is that it is a fixpoint of the union of valuations (function \(f\) defined below) that contains the initial valuation:
 \begin{align*}
-	f\mpar{p} = s' \mapsto p\mpar{s'} \vee \bigsymb{\bigvee_\subbox{\OTg \,\in\, \fIT{s'}}} p\mpar{s}\psubst{\psi} \wedge g &&
+	f\mpar{p} = \mbrc{s' \mapsto p\mpar{s'} \vee \bigsymb{\bigvee_\subbox{\OTg \,\in\, \fIT{s'}}} p\mpar{s}\psubst{\psi} \wedge g} &&
 	\sigma_0 \vdash \reach{A}\mpar{s_0} &&
@@
 \begin{defi}[Non-locking composition, intuitive definition]
-The composition  \(A_p\subst{A_c}{k} = \OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(A_c \defobject \OA{S_c}{s_{0c}}{V_c}{\sigma_{0c}}{J_c}{T_c}\), \(A_p \defobject \OA{S_p}{s_{0p}}{V_p}{\sigma_{0p}}{J_p}{T_p}\) and \(k \in J_p\), is a non-locking composition if there is a reachability predicate such that from reachable configurations, either a transition is possible in \(A_p\subst{A_c}{k}\) or there were no possible transition in \(A_p\) to begin with
+Let  \(A \defobject A_p\subst{A_c}{k} = \OA{S}{s_0}{V}{\sigma_0}{J}{T}\) be the composition of \(A_c \defobject \OA{S_c}{s_{0c}}{V_c}{\sigma_{0c}}{J_c}{T_c}\), in the hole \(k \in J_p\) of \(A_p \defobject \OA{S_p}{s_{0p}}{V_p}{\sigma_{0p}}{J_p}{T_p}\).
+The composition is non-locking if there is a reachability predicate such that from reachable configurations, if there was a possible transition in \(A_p\) then there is a possible transition in \(A_p\subst{A_c}{k}\):
 \begin{multline*}
-	\forall s \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A_p\subst{A_c}{k}}\mpar{s}} \implies \mpar{\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t}} \\
-	\vee \forall t_p \in \fOT{\pi_{S_p}\mpar{s}}, \forall \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \nvdash \fguard{t_p}
+	\forall \mpar{s_p, s_c} \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A_p\subst{A_c}{k}}\mpar{s}} \implies \\
+	\mpar{\exists t_p \in \fOT{s_p}, \exists \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \vdash \fguard{t_p}} \implies \\
+	\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t}
 \end{multline*}
 \end{defi}
-(\(\pi_X\) is the projection of tuples on the set \(X\)). % TODO: Move that to the notations
+An illustration of the introduction of a deadlock by composition and the definition of non-locking composition is given in Appendix \ref{apx:lockcomp}.
 
-To illustrate the introduction of a deadlock in a composition and the definition of non-locking composition, we consider the following example.
-\begin{exi}[Deadlocks introduced by composition]
-\Ludo{TODOludo}{lire l'explication}
-This example reuses the counter introduced in Figure \ref{fig:tlh}.
-The behaviour of the counter is to count external \(\act{tick}\) actions up to the amount set by action \(\act{set}\mpar{x}\) then to notify the environnement that this amount of time elapsed.
-In the traffic light example the clock is not specified, we will introduce deadlocks using a wisely choosen clock specification.
-However the full traffic light will not be used in order to simplify the example, only the counter will be.
-
-\begin{figure}
-\input{randomtick_clock.tex}
-\vrule
-\input{register_anytick.tex}
-\caption{On the left: A clock which imposes a tick; On the right: A modified version of the counter at figure \ref{fig:tlh}}
-\label{fig:anytick}
-\end{figure}
-The clock on the left side of Figure \ref{fig:anytick} transmit the actions of its hole unchanged until the clock imposes a \(\act{tick}\) on its hole.
-This can model a physical clock, because physical time ticks cannot be delayed.
-
-If the hole cannot handle a \(\act{tick}\) at any time then there is a deadlock, which is the case with our counter.
-The composition of this clock with the counter is given on the left of Figure \ref{fig:deadlock}.
-\begin{figure}
-\input{Composition_deadlock.tex}
-\vrule
-\input{Composition_nolock.tex}
-\caption{On the left: Deadlocks introduced by composition; On the right: No deadlock introduced by composition}
-\label{fig:deadlock}
-\end{figure}
-There are two deadlocks:
-The first is in the state \(1S\), which correspond to the clock trying to imppose a tick when the counter is not set.
-The second is in the state \(1C\), which correspond to the clock trying to impose a tick when the counter has reached the amount peviously set, but not has not yet reported it to the environment.
-These deadlocks could have been in the specification in which case they were intended, but it is not the case here.
-
-The counter on the right of Figure \ref{fig:anytick} is a modification to accept ticks at in any state.
-Composing this modified counter gives the automaton on the right of Figure \ref{fig:deadlock} which has no deadlocks.
-
-We should successfully caracterise the second composition as non-locking but fail for the first.
-\begin{itemize}
-\item In the state \(0S\) any valuation is reachable (no initial valuation).
-	In both automata the transition \nmm{\OT{0S}{1S}{\tau}{\mbrc{}}{\top}{\mbrc{}}} has a true guard, hence the first branch of the disjunction holds.
-\item In the state \(0C\), for the left automaton, valuations where \(t \geq c \geq 0 \vee \mpar{t < 0 \wedge c = 0}\) are reachable; for the right automaton, valuations where \(c \geq 0\) are reachable.
-	For all these valuations the transition \nmm{\OT{0C}{1C}{\tau}{\mbrc{}}{\top}{\mbrc{}}} has a true guard, hence the first branch of the disjunction holds.
-\item In the state \(1C\), the same valuations as the ones reachable in \(0C\) are also reachable.
-	In the right automaton the transition \nmm{\OT{1C}{0C}{\act{tick}}{\mbrc{}}{\top}{\mbrc{c \gets c + 1}}} has a true guard.
-	In the left automaton the transition \nmm{\OT{1C}{0C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} covers the cases where \(c < t\).
-	For the other cases (\(c = t \vee t \leq 0 \mbrk{\leq c}\)) there are no transition with a true guard, and in the clock the transition same transition as for the state \(1S\) has a true guard, hence the composition is not non-locking.
-\item In the state \(1S\) any valuation is reachable.
-	In the left automaton, no transition is possible, and in the parent automaton \nmm{\OT{1}{0}{\act{tick}}{\mbrc{H \mapsto \act{tick}}}{\top}{\mbrc{}}} had a true guard, so the composition is not a non-locking composition (we already know it at this point).
-	In the right automaton, \nmm{\OT{1S}{0S}{\act{tick}}{\mbrc{}}{\top}{\mbrc{}}} has a true guard.
-\end{itemize}
-The left automaton indeed fails at being the result of a non-locking composition where the right automaton passes.
-
-One more thing worth noting is that for the left automaton, in the state \(1C\) with a valuation such that \(t < 0\), the counter agent is in a deadlock state.
-We could have defined the non-locking composition so that this is considered as an intended deadlock, making the requirement symetric.
-However the the semantics of composition in a hole is assymetric and the considered specification -as in the deadlock reduction- is the parent automaton.
-A symetric version is presented in Section ???\marginpar{TODO LATER}, where we introduce a more symetric model of open automata.
-\end{exi}
-
-When expanding the aliases \(S, s_0, V\) in \Ludo{the definition}{which def?
-pas lu la suite car je savais pas ou ca allait}, and remarking that the last existential quantifier can be unfolded into a transition in \(A\) and one in \(A_p\) with the added condition that they match, the definition become mildly similar with the deadlock reduction one.
-% TODO: Make it clearer, what expansion, what is the result; or remove
+We can expand the aliases \(S, V\) into \(S_p \times S_c, V_p \uplus V_c\) and the last transition \(t\) into a pair \(\mpar{t_p, t}\) where the first transition is the one from \(A_p\) which generated \(t\).
+Doing that makes the definition become mildly similar with the deadlock reduction one.
 It is not a coincidence because their goal is to caracterise the same kind of compatibility between automata.
 Actually it is possible to simplify both definition and make them even more similar.
-
 \begin{defi}[Deadlock reduction, working definition]
@@
 \section{Refinement relations in restricted cases}\label{sec:prelref}
+% Mettre des sets de noms en commun qu'on veut effectivement mapper pour la transitivité
 The main goal of this section is to help the reader understand the problems, constraints and different elements involved to solve them so that they are not all introduced at once in the real refinement relation.
@@
 \section{Future work}
+% TODO: Weak variants, tau-stuttering, livelocks
+% Other kind of refinement relation that \Quentin{I may explore}{This is a note for possible path, some may be explored, some may not.} are control refinement/hole refinement\footnote{No good formulation atm, the idea is that \(a \leq b \defnotation sth \wedge J_a \setminus J_b \leq_{ctrl} J_b \setminus J_a\), sth is probably a clause to ensure that they behave the same without holes involved.}, (meet semi)lattice refinement\footnote{meet = handshake, \(a \leq b \defnotation a = a || b\) with sync holes, I think this will be equivalent to hole-identical sim, (join=non-det choice?)}, weak-simulation refinement\footnote{Weak variation for each interesting simulation refinement}, composition-correct refinement\footnote{Basically a stricter variant of simulation-refinement where simulation has to take place the other way for some transitions (no different holes?) in order to be correct wrt composition}.
 
@@
 
-\section{Proof of equivalent definitions}\label{apx:lemeqd}
+\section{Example of deadlock introduced by composition and requirements of non-locking composition}\ref{apx:lockcomp}
+\begin{exi}[Deadlocks introduced by composition]
+\Ludo{TODOludo}{lire l'explication}
+This example reuses the counter introduced in Figure \ref{fig:tlh}.
+The behaviour of the counter is to count external \(\act{tick}\) actions up to the amount set by action \(\act{set}\mpar{x}\) then to notify the environnement that this amount of time elapsed.
+In the traffic light example the clock is not specified, we will introduce deadlocks using a wisely choosen clock specification.
+However the full traffic light will not be used in order to simplify the example, only the counter will be.
+
+\begin{figure}
+\input{randomtick_clock.tex}
+\vrule
+\input{register_anytick.tex}
+\caption{On the left: A clock which imposes a tick; On the right: A modified version of the counter at figure \ref{fig:tlh}}
+\label{fig:anytick}
+\end{figure}
+The clock on the left side of Figure \ref{fig:anytick} transmit the actions of its hole unchanged until the clock imposes a \(\act{tick}\) on its hole.
+This can model a physical clock, because physical time ticks cannot be delayed.
+
+If the hole cannot handle a \(\act{tick}\) at any time then there is a deadlock, which is the case with our counter.
+The composition of this clock with the counter is given on the left of Figure \ref{fig:deadlock}.
+\begin{figure}
+\input{Composition_deadlock.tex}
+\vrule
+\input{Composition_nolock.tex}
+\caption{On the left: Deadlocks introduced by composition; On the right: No deadlock introduced by composition}
+\label{fig:deadlock}
+\end{figure}
+There are two deadlocks:
+The first is in the state \(1S\), which correspond to the clock trying to imppose a tick when the counter is not set.
+The second is in the state \(1C\), which correspond to the clock trying to impose a tick when the counter has reached the amount peviously set, but not has not yet reported it to the environment.
+These deadlocks could have been in the specification in which case they were intended, but it is not the case here.
+
+The counter on the right of Figure \ref{fig:anytick} is a modification to accept ticks at in any state.
+Composing this modified counter gives the automaton on the right of Figure \ref{fig:deadlock} which has no deadlocks.
+
+We should successfully caracterise the second composition as non-locking but fail for the first.
+\begin{itemize}
+\item In the state \(0S\) any valuation is reachable (no initial valuation).
+	In both automata the transition \nmm{\OT{0S}{1S}{\tau}{\mbrc{}}{\top}{\mbrc{}}} has a true guard, hence the first branch of the disjunction holds.
+\item In the state \(0C\), for the left automaton, valuations where \(t \geq c \geq 0 \vee \mpar{t < 0 \wedge c = 0}\) are reachable; for the right automaton, valuations where \(c \geq 0\) are reachable.
+	For all these valuations the transition \nmm{\OT{0C}{1C}{\tau}{\mbrc{}}{\top}{\mbrc{}}} has a true guard, hence the first branch of the disjunction holds.
+\item In the state \(1C\), the same valuations as the ones reachable in \(0C\) are also reachable.
+	In the right automaton the transition \nmm{\OT{1C}{0C}{\act{tick}}{\mbrc{}}{\top}{\mbrc{c \gets c + 1}}} has a true guard.
+	In the left automaton the transition \nmm{\OT{1C}{0C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} covers the cases where \(c < t\).
+	For the other cases (\(c = t \vee t \leq 0 \mbrk{\leq c}\)) there are no transition with a true guard, and in the clock the transition same transition as for the state \(1S\) has a true guard, hence the composition is not non-locking.
+\item In the state \(1S\) any valuation is reachable.
+	In the left automaton, no transition is possible, and in the parent automaton \nmm{\OT{1}{0}{\act{tick}}{\mbrc{H \mapsto \act{tick}}}{\top}{\mbrc{}}} had a true guard, so the composition is not a non-locking composition (we already know it at this point).
+	In the right automaton, \nmm{\OT{1S}{0S}{\act{tick}}{\mbrc{}}{\top}{\mbrc{}}} has a true guard.
+\end{itemize}
+The left automaton indeed fails at being the result of a non-locking composition where the right automaton passes.
+
+One more thing worth noting is that for the left automaton, in the state \(1C\) with a valuation such that \(t < 0\), the counter agent is in a deadlock state.
+We could have defined the non-locking composition so that this is considered as an intended deadlock, making the requirement symetric.
+However the the semantics of composition in a hole is assymetric and the considered specification -as in the deadlock reduction- is the parent automaton.
+A symetric version of composition on a flat model of open automata is presented in Section ???\marginpar{TODO LATER}.
+\end{exi}
+
+\section{Proof of equivalent definitions}\label{apx:lemeqd} % TODO: fix the proofs about the switch \vee -> \implies
 

### 2021-05-20 2021-Refinement/report.tex
Section 5 rework

@@
 The \(\act{accept}\) action is shortened as \(\act{acc}\) in the examples.
-During the synchronised action \Quentin{data can be exchanged}{I need to read a little bit more on that; is that a return code?}.
+During the synchronised action, the value returned by first agent is passed to the second agent.
 \begin{exi}[Enable, state-oriented]
@@
 \end{align*}
-Similarly to expression substitution, the parallel composition is noted \(A\psubst{A_j^{j \in J}}\).
 \end{defi}
@@
 
-An example of composition can be found in Appendix \ref{apx:composition}.
 Composition is a complex process that generates big automata with complex and potentially simplifiable transitions.
 However simplification is a hard problem that is not yet automatised on open automata, so from this point the guards and transitions will always be simplified by hand without further explaination.
+An example of composition can be found in Appendix \ref{apx:composition}.
+\begin{prop}[Parallel composition]
+Let \(A_1\), \(A_2\), \(A_3\) be three open automata with respectively \(J_1\), \(J_2\) and \(J_3\) as hole names.
+We have
+\begin{align*}
+	A_1\subst{A_2}{j}\subst{A_3}{j'} & = A_1\subst{A_3}{j'}\subst{A_2}{j} & j, j' & \in J_1 \\
+	A_1\subst{A_2}{j_1}\subst{A_3}{j_2} & = A_1\subst{A_2\subst{A_3}{j_2}}{j_1} & \mpar{j_1, j_2} & \in J_1 \times J_2
+\end{align*}
+Where the equality is modulo isomorphism (state renaming, associativity, commutativity).
+\end{prop}
+This propriety is induced by the composition on open pNets. % LATER: proof?
+Intuitively it holds because the cartesian product of states, the union of sets, the union of maps and the conjunction on formulas (in the guards) are commutative and associative.
+This allows us to define the parallel composition \(A\psubst{A_j^{j \in J'}}\) if there is any order of (sequential) composition where each \(A_j\) is composed in the hole \(j\).
 
-% TODO HERE: relecture
 \section{Properties of a refinement relation for Open Automata}\label{sec:proofelts}
@@
 For example if we are interested in producing the same sequences of actions as another automaton we may want to use trace set inclusion as a refinement.
-Here the main expected properties are related to composition and action refinement. % LATER: explain here or remove if not tackled
+Here the main expected properties are related to composition and action refinement. % LATER: explain action refinement here or remove if not tackled
 Because of composition, a relation as strong as simulation must be used as observed in the articles about FH-bisimulation \cite{henrio:01055091}.
@@
 The important properties we consider for the relation on states are being a simulation and the reduction of deadlocks as defined in the following definitions.
-\begin{defi}[Pre-simulation on open automata] % TODO: Is the definition satifying now?
+\begin{defi}[Pre-simulation on open automata]
+\Quentin{}{Is the definition satisfying now?}
 For two automata \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), a relation under predicate \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a pre-simulation if it satisfies both
@@
 By preventing them we could hope that the refinement preserves some liveness properties.
-\begin{defi}[Deadlock reduction, intuitive definition] % TODO HERE: repasser a un implique
+\begin{defi}[Deadlock reduction, intuitive definition]
 A relation under predicate \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if:
@@
 \end{defi}
-
 For the reader not used to simulations and bisimulations, this definition of a predicate can seem strange.
@@
 \begin{defi}[Non-locking composition, intuitive definition]
-Let  \(A \defobject A_p\subst{A_c}{k} = \OA{S}{s_0}{V}{\sigma_0}{J}{T}\) be the composition of \(A_c \defobject \OA{S_c}{s_{0c}}{V_c}{\sigma_{0c}}{J_c}{T_c}\), in the hole \(k \in J_p\) of \(A_p \defobject \OA{S_p}{s_{0p}}{V_p}{\sigma_{0p}}{J_p}{T_p}\).
+Let  \(A_p\subst{A_c}{k} = \OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(A_c \defobject \OA{S_c}{s_{0c}}{V_c}{\sigma_{0c}}{J_c}{T_c}\), \(A_p \defobject \OA{S_p}{s_{0p}}{V_p}{\sigma_{0p}}{J_p}{T_p}\) and \(k \in J_p\).
 The composition is non-locking if there is a reachability predicate such that from reachable configurations, if there was a possible transition in \(A_p\) then there is a possible transition in \(A_p\subst{A_c}{k}\):
@@
 \begin{defi}[Deadlock reduction, working definition]
-A simulation \(\leq\) is deadlock reducing if in all the \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) such that \(\wrel{A_1}{A_2}{R}\), there is one that also satisfies
+A relation under predicate \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if it is a pre-simulation and:
 \begin{multline*}
@@
 \end{defi}
-% TODO: Explain this formulations (it will also do the job of explaining the definition below)
+The requirement here is that from any configuration related configurations, if there is a possible transition in the second automaton (whatever the value of the free variables) then there is a possible transition in the first automaton (the existential quantifier is implicit in the notation \(\vdash\)).
+The transition are not matched because the relation under predicate is a pre-simulation and it is sufficient to ensure it as will be shown in the proof.
+Apart from the matching transitions this is exactly the same explaination as the intuitive definition.
+The expected advantage of this formulation is that a SMT should behave better without the quantifiers.
+Indeed the big disjunctions are not quantifiers because in practise the out-transitions are finitary, and so is the expansion of the disjunction.
 \begin{lem}
@@
 
-This new substitution can replace the standard substitution in the case where only one hole is filled and also in the parallel case.
-In the parallel case the condition is checked after the parallel substitution because there is no guarantee that any order of sequential composition is non-locking for every substitution even if the parallel substitution is non-locking.
-%\begin{exi} % TODO
-%\begin{figure}
-%\centering
-%\input{}
-%\vrule
-%\input{}
-%\vrule
-%\input{}
-%\caption{}
-%\label{fig:pnls}
-%\end{figure}
-% An example of non-locking parallel substitution where no individual substitution is non-locking is given in Figure \ref{fig:pnls}.% TODO HERE
-%\end{exi}
+This new definition of composition can replace the standard composition in the case where only one hole is filled, and also in the parallel case.
+In the parallel case, the condition is checked after the parallel composition because there is no guarantee that any order of sequential composition is non-locking, even if the parallel composition is non-locking.
+However the oppsite way is true even if uninformative:
+If there is an order of composition where every composition is non-locking then the last composition is non-locking, last composition resulting in the same automaton as the parallel composition.
+\begin{exi} % TODO HERE: TIKZ
+\begin{figure}
+\centering
+\input{svn_rollingrelease.tex}
+\caption{A made-up protocol for file synchronisation}
+\label{fig:pnls}
+\end{figure}
+The automaton on Figure \ref{fig:pnls} is a sample protocol for file synchronisation.
+The two holes are \(net\) a network manager used to perform operations on the network, and \(hash\) a file integrity check used to generate a fingerprint.
+The state \(i\) is the initial state.
+In that state we want to synchronise the files before working, or work on the local version as a fallback.
+If the preferred version is the remote one, we go in state \(d1\) asking the netwotk manager to fetch the lastest version, then ask the integrity checker to validate the fingerprint.
+If the preferred version is the local one, we go in state \(d2\) asking for the integrity checker to generate a fingerprint for the local files, then ask the network manager to push them.
+In fallback we use the local version.
+
+Suppose that actually the network manager is reliable and the integrity check is only used to generate a fingerprint.
+Someone may in that case eliminate the blue transitions as an optimization.
+Once the blue transition eliminated, we can debranch the network manager and the file integrity check, but always at the same time.
+The composition with a deadlock automaton in both holes (debranching) is non-locking, but any individual composition is locking.
+\end{exi}
 From this point and in the previous definitions, composition will only refer to non-locking composition.
 
-The relations will have to be at least preorders, simulations and prevent the introduction of deadlocks to be called refinement simulation.
-With all these properties we can now look at some concrete refinemet relations.
+A relation on open automata and its corresponding relation under predicate are simulations if the latter is a deadlock reducing pre-simulations and the former is a preorder.
+With all these properties we can now look at some concrete refinement relations.
 
@@
 
-\section{Example of deadlock introduced by composition and requirements of non-locking composition}\ref{apx:lockcomp}
+\section{Example of deadlock introduced by composition and requirements of non-locking composition}\label{apx:lockcomp}
 \begin{exi}[Deadlocks introduced by composition]

### 2021-05-20 2021-Refinement/svn_rollingrelease.tex
Section 5 rework

\begin{tikzpicture}

\node[state,initial] (v0) at (0,0) {i};
\node[state] (vd1) at (0,2.5) {d1};
\node[state] (vd2) at (0,-2.5) {d2};
\node[state] (vop) at (6,0) {op};

\draw (v0) edge node[near end] {\OTd{\act{local}}{}{}} (vop);
\draw (v0) edge[bend left,looseness=0] node {\OTd{\act{fetch}}{net \mapsto \act{fetched}}{}} (vd1);
\draw (vd1) edge[blue,bend left,looseness=0] node {\OTd{\act{err}}{hash \mapsto \act{invalid}}{}} (v0);
\draw (v0) edge[bend left,looseness=0] node {\OTd{\act{valid}}{hash \mapsto \act{valid}}{}} (vd2);
\draw (vd2) edge[blue,bend left,looseness=0] node {\OTd{\act{err}}{net \mapsto \act{timeout}}{}} (v0);
\draw (vd1) edge[bend left] node[near end] {\OTd{\act{valid}}{hash \mapsto \act{valid}}{}} (vop);
\draw (vd2) edge[bend right] node[near end,'] {\OTd{\act{push}}{net \mapsto \act{pushed}}{}} (vop);

\end{tikzpicture}

### 2021-05-21 2021-Refinement/report.tex
Fixed appendix proofs and example 3

@@
 % TODO: CITER LES CONFERENCES
+% Proof sketch
 
@@
 Here we assume that one of the related open automata can be obtained by composing an open automaton in a hole, open automaton which can have holes itself.
-This implies that there is no relation between their holes (\(J \setminus \mset{k_i}{i \in \mdbrk{1; n}} \bigcup_{i \in \mdbrk{1; n}} J_i\) is neither subset nor superset of \(J_p\)).
+This implies that there is no relation between their holes (\(J \setminus \mset{k_i}{i \in \mdbrk{1; n}} \cup \bigcup_{i \in \mdbrk{1; n}} J_i\) is neither subset nor superset of \(J_p\)).
 Yet we still assume that in holes with the same name, the same open automaton will be composed.
@@
 \begin{multline*}
-	\forall \mpar{s_p, s_c} \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A_p\subst{A_c}{k}}\mpar{s}} \implies \\
+	\forall s \defobject \mpar{s_p, s_c} \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A_p\subst{A_c}{k}}\mpar{s}} \implies \\
 	\mpar{\exists t_p \in \fOT{s_p}, \exists \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \vdash \fguard{t_p}} \implies \\
@@
 The composition \(A \defobject A_p\subst{A_c}{k}\) is a non-locking composition if:
-\[ \forall s \in S, \forall \sigma: V \uplus \bigcup_\subbox{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fvars{t_p} \to \values, \sigma \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
+\[ \forall ss \defobject \mpar{s_p, s_c} \in S, \forall \sigma: V \uplus \bigcup_\subbox{t_p \in \fOT{s_p}} \fvars{t_p} \to \values, \sigma \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
 \end{defi}
@@
 This new definition of composition can replace the standard composition in the case where only one hole is filled, and also in the parallel case.
-In the parallel case, the condition is checked after the parallel composition because there is no guarantee that any order of sequential composition is non-locking, even if the parallel composition is non-locking.
+In the parallel case, we may think that if the condition is checked in the parallel case (at the final composition), then the composition is non-locking for every composition order.
+It is not true.
+Actually even if the last composition is non-locking there is no guarantee that there is an order of sequential composition that is non-locking at every step.
 However the oppsite way is true even if uninformative:
 If there is an order of composition where every composition is non-locking then the last composition is non-locking, last composition resulting in the same automaton as the parallel composition.
-\begin{exi} % TODO HERE: TIKZ
+So the condition is better checked after the parallel composition or the last individual composition.
+\begin{exi}
 \begin{figure}
@@
 
-Suppose that actually the network manager is reliable and the integrity check is only used to generate a fingerprint.
-Someone may in that case eliminate the blue transitions as an optimization.
-Once the blue transition eliminated, we can debranch the network manager and the file integrity check, but always at the same time.
-The composition with a deadlock automaton in both holes (debranching) is non-locking, but any individual composition is locking.
+We can debranch the network manager and the file integrity check by composing a deadlock automaton in their holes, but always both at the same time.
+The reason for that is the parallel composition is non-locking, but any individual composition is locking because the state \(d1\) or \(d2\) (depending on the order) becomes a deadlock.
 \end{exi}
@@
 
-\section{Proof of equivalent definitions}\label{apx:lemeqd} % TODO: fix the proofs about the switch \vee -> \implies
+\section{Proof of equivalent definitions}\label{apx:lemeqd}
 
 \subsection{Proof of lemma 1}
-\begin{proof}
-Let \(R\), \(A_1 \defobject \OA{S_1}{s_{01}}{V_1}{\sigma_{01}}{J_1}{T_1}\), \(A_2 \defobject \OA{S_2}{s_{02}}{V_2}{\sigma_{02}}{J_2}{T_2}\) be such that:
-\[ \wrel{A_1}{A_2}{R} \hyp{0} \]
+Let \(R\) be a pre-simulation between \(A_1 \defobject \OA{S_1}{s_{01}}{V_1}{\sigma_{01}}{J_1}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{V_2}{\sigma_{02}}{J_2}{T_2}\).
 We want to prove:
@@
 	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \to \values, \mpar{\sigma \vdash R\mpar{s_1, s_2}} \implies \\
-	\mpar{\everymath{\displaystyle}\begin{array}{c}
-		\bigsymb{\exists} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_1} \uplus \fvars{t_2} \to \values, \\
-		\sigma \uplus \nu \vdash g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
-	\end{array}} \\
-	\vee \forall t_2 \in \fOT{s_2}, \forall \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \nvdash \fguard{t_2} \tag{ID}\label{eq:drID}
+	\mpar{\exists t_2 \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \vdash \fguard{t_2}} \implies \\
+	\bigsymb{\exists} \mpar{t_1, t_2} \defobject \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2}, \exists \nu: \fvars{t_1} \uplus \fvars{t_2} \to \values, \\
+	\sigma \uplus \nu \vdash g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}\tag{ID}\label{eq:drID}
 \end{multline}
+\begin{proof}
 \item[\(\eqref{eq:drWD}\Rightarrow\eqref{eq:drID}\):]
@@
 	\[ \sigma \vdash R\mpar{s_1, s_2} \hyp{1} \]
-	By excluded middle, either the right hand side of the disjunction in (\ref{eq:drWD}) holds, in which case the property holds, or it doesn't hold and we have the hypothesis:
+	We admit the left side of the second implication in \eqref{eq:drID}:
 	\[ \exists t_2 \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \vdash \fguard{t_2} \hyp{2} \]
-	We get immediately the values \(t_2\), \(\nu\) and the hypothesis:
+	And get immediately the values \(t_2\), \(\nu\) and the hypothesis:
 	\[ \sigma \uplus \nu \vdash \fguard{t_2} \hyp{2'} \]
-	\(R\) satisfies (\ref{eq:drWD}) with the current value of \(\mpar{s_1, s_2}\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \(\bigcup_{t_2 \in \fOT{s_2}} \fguard{t_2}\) so we have:
+	\(R\) satisfies \eqref{eq:drWD} with the current value of \(\mpar{s_1, s_2}\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \(\bigcup_{t_2 \in \fOT{s_2}} \fguard{t_2}\) so we have:
 	\[ \sigma \uplus \nu \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{3} \]
@@
 	\[ \sigma \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{2'} \]
-	To do that we use (\ref{eq:drID}) with the current value of \(\mpar{s_1, s_2}\) and \(\sigma\), and prove the premisse of the implication with \hyp{4} to get:
+	To do that we use \eqref{eq:drID} with the current value of \(\mpar{s_1, s_2}\) and \(\sigma\), and prove the premisse of the implication with \hyp{4} to get:
 	\begin{multline}
-		\mpar{\everymath{\displaystyle}\begin{array}{c}
+		\mpar{\exists t_2 \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \vdash \fguard{t_2}} \implies \\
 		\bigsymb{\exists} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_1} \uplus \fvars{t_2} \to \values, \\
-			\sigma \uplus \nu \vdash g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
-		\end{array}} \\
-		\vee \forall t_2 \in \fOT{s_2}, \forall \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \nvdash \fguard{t_2} \hyp{6}
+		\sigma \uplus \nu \vdash g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \hyp{6}
 	\end{multline}
-	There are two cases in this disjunction, the second is in contradiction with \hyp{5} and the first gives \(t_1\), \(t'_2\) and \(\nu\) such that (only the interesting part of the conjunction has been extracted):
+	The left part of the implication is proved for \(t_2\) and \(\sigma\) (for the values covered by \(\nu\)) with \hyp{5}.
+	The right part gives \(t_1\), \(t'_2\) and \(\nu\) such that (only the interesting part of the conjunction has been extracted):
 	\[ \sigma \uplus \nu \vdash \fguard{t_1} \hyp{7} \]
@@
 \subsection{Proof of lemma 2}
+We want to prove
+\[ \forall s \defobject \mpar{s_p, s_c} \in S, \forall \sigma: V \uplus \bigcup_\subbox{t_p \in \fOT{s_p}} \fvars{t_p} \to \values, \sigma \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \tag{WD}\label{eq:nlcWD} \]
+\[ \iff \]
+\begin{multline*}
+	\forall s \defobject \mpar{s_p, s_c} \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A}\mpar{s}} \implies \\
+	\mpar{\exists t_p \in \fOT{s_p}, \exists \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \vdash \fguard{t_p}} \implies \\
+	\mpar{\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t}} \tag{ID}\label{eq:nlcID}
+\end{multline*}
 \begin{proof}
-\[ \forall s \in S, \forall \sigma: V \uplus \bigcup_\subbox{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fvars{t_p} \to \values, \sigma \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \tag{WD}\label{eq:nlcWD} \]
-\[ \iff \]
-\begin{multline*}
-	\forall s \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A}\mpar{s}} \implies \mpar{\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t}} \\
-	\vee \forall t_p \in \fOT{\pi_{S_p}\mpar{s}}, \forall \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \nvdash \fguard{t_p} \tag{ID}\label{eq:nlcID}
-\end{multline*}
 \item[\(\eqref{eq:nlcWD}\Rightarrow\eqref{eq:nlcID}\):]
-	Let \(s \in S\) and \(\sigma \in V \to \values\) be such that:
+	Let \(s \defobject \mpar{s_p, s_c} \in S\) and \(\sigma \in V \to \values\) be such that:
 	\[ \sigma \vdash \reach{A}\mpar{s} \hyp{1} \]
-	By excluded middle, either the right hand side of the disjunction in (\ref{eq:nlcWD}) holds, in which case the property holds, or it doesn't hold and we have the hypothesis:
-	\[ \exists t_p \in \fOT{\pi_{S_p}\mpar{s}}, \exists \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \vdash \fguard{t_p} \hyp{2} \]
+	We admit the left side of the second implication in \eqref{eq:nlcID}:
+	\[ \exists t_p \in \fOT{s_p}, \exists \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \vdash \fguard{t_p} \hyp{2} \]
 	We get immediately the values \(t_p\), \(\nu\) and the hypothesis:
 	\[ \sigma \uplus \nu \vdash \fguard{t_p} \hyp{2'} \]
-	\(R\) satisfies (\ref{eq:nlcWD}) with the current value of \(s\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \(\bigcup_{t_p \in \fOT{\pi_{s_p}\mpar{s}}} \fguard{t_p}\) so we have:
-	\[ \sigma \uplus \nu \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{3} \]
+	\(R\) satisfies \eqref{eq:nlcWD} with the current value of \(s\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \(\bigcup_{t_p \in \fOT{s_p}} \fguard{t_p}\) so we have:
+	\[ \sigma \uplus \nu \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{3} \]
 	The \(\vdash\) hides an implicit \(\exists\) that we use to get values to the variables in \(\bigcup_{t \in \fOT{s}}\) in a valuation \(\mu\).
@@
 \item[\(\eqref{eq:nlcWD}\Leftarrow\eqref{eq:nlcID}\):]
-	Let \(s \in S\), \(\sigma \in V \uplus \bigcup_{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fvars{t_p} \to \values\).
+	Let \(s \defobject \mpar{s_p, s_c} \in S\), \(\sigma \in V \uplus \bigcup_{t_p \in \fOT{s_p}} \fvars{t_p} \to \values\).
 	We want to prove:
-	\[ \sigma \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{\pi_{S_p}\mpar{s}}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \goal{1} \]
+	\[ \sigma \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \goal{1} \]
 	We can admit the left part of the implication in which we decompose the big disjunction to get \(t_p\) and:\\
@@
 	\[ \sigma \vdash \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \goal{1'} \]
-	To do that we use (\ref{eq:nlcID}) with the current value of \(s\) and \(\sigma\), and prove the premisse of the implication with \hyp{4} to get:
+	To do that we use \eqref{eq:nlcID} with the current value of \(s\) and \(\sigma\), and prove the premisse of the implication with \hyp{4} to get:
 	\begin{multline}
-		\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t} \\
-		\vee \forall t_p \in \fOT{\pi_{S_p}\mpar{s}}, \forall \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \nvdash \fguard{t_p} \hyp{6}
+		\mpar{\exists t_p \in \fOT{s_p}, \exists \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \vdash \fguard{t_p}} \implies \\
+		\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t} \hyp{6}
 	\end{multline}
-	There are two cases in this disjunction, the second is in contradiction with \hyp{5} and the first gives \(t\) and \(\nu\) such that:
+	The left part of the implication is proved for \(t_p\) and \(\sigma\) (for the values covered by \(\nu\)) with \hyp{5}.
+	The right part gives \(t\) and \(\nu\) such that:
 	\[ \sigma \uplus \nu \vdash \fguard{t} \hyp{7} \]

### 2021-05-25 2021-Refinement/file_sync.tex
Hole-identical refinement definition

--- 2021-05-20 2021-Refinement/svn_rollingrelease.tex
@@
 \draw (v0) edge[bend left,looseness=0] node {\OTd{\act{fetch}}{net \mapsto \act{fetched}}{}} (vd1);
-\draw (vd1) edge[blue,bend left,looseness=0] node {\OTd{\act{err}}{hash \mapsto \act{invalid}}{}} (v0);
+\draw (vd1) edge[bend left,looseness=0] node {\OTd{\act{err}}{hash \mapsto \act{invalid}}{}} (v0);
 \draw (v0) edge[bend left,looseness=0] node {\OTd{\act{valid}}{hash \mapsto \act{valid}}{}} (vd2);
-\draw (vd2) edge[blue,bend left,looseness=0] node {\OTd{\act{err}}{net \mapsto \act{timeout}}{}} (v0);
+\draw (vd2) edge[bend left,looseness=0] node {\OTd{\act{err}}{net \mapsto \act{timeout}}{}} (v0);
 \draw (vd1) edge[bend left] node[near end] {\OTd{\act{valid}}{hash \mapsto \act{valid}}{}} (vop);

### 2021-05-25 2021-Refinement/report.tex
Hole-identical refinement definition

@@
 Here we assume that one of the related open automata can be obtained by composing an open automaton in a hole, open automaton which can have holes itself.
-This implies that there is no relation between their holes (\(J \setminus \mset{k_i}{i \in \mdbrk{1; n}} \cup \bigcup_{i \in \mdbrk{1; n}} J_i\) is neither subset nor superset of \(J_p\)).
+This implies that there is no relation between their holes, \(J = \mpar{J_p \uplus \biguplus_{i \in \mdbrk{1; n}} J_i} \setminus \mset{k_i}{i \in \mdbrk{1; n}} \) is neither subset nor superset of \(J_p\).
 Yet we still assume that in holes with the same name, the same open automaton will be composed.
@@
 \begin{multline*}
-	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \uplus \bigcup_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values, \\
+	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values, \\
 	\sigma \vdash \mpar{R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
@@
 The composition \(A \defobject A_p\subst{A_c}{k}\) is a non-locking composition if:
-\[ \forall ss \defobject \mpar{s_p, s_c} \in S, \forall \sigma: V \uplus \bigcup_\subbox{t_p \in \fOT{s_p}} \fvars{t_p} \to \values, \sigma \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
+\[ \forall ss \defobject \mpar{s_p, s_c} \in S, \forall \sigma: V \uplus \biguplus_\subbox{t_p \in \fOT{s_p}} \fvars{t_p} \to \values, \sigma \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
 \end{defi}
@@
 \centering
-\input{svn_rollingrelease.tex}
+\input{file_sync.tex}
 \caption{A made-up protocol for file synchronisation}
@@
 
-% TODO: re-ecriture
+% Mettre des sets de noms en commun qu'on veut effectivement mapper pour la transitivité
+% J'2 \subseteq J'1 in hole-subset, J'1 \subseteq J'2 in hole-superset (decide of transition variable with holes); composition with new holes is hole-subset where hole variables are free then hole-superset where hole names have no conflicts with removed holes.
+Transitivity must ensure holes name have no conflict for that reason!
 \section{Refinement relations in restricted cases}\label{sec:prelref}
-% Mettre des sets de noms en commun qu'on veut effectivement mapper pour la transitivité
-The main goal of this section is to help the reader understand the problems, constraints and different elements involved to solve them so that they are not all introduced at once in the real refinement relation.
-The main objective of the refinement relations \Ludo{in this section}{du coup la on se pose la question est ce juste ici ou est ce le but global, c est quio le schema general?
-ceci dit ca sera peut etre resolu par l introduction ...
-mais dans tous les cas une petite couche sur ou on est et ou on va ca serait bien.
-il faut quelque part clairemetn definir ce qu on veut et sous quelle condition plus tot que ici} is to be able to state that a composition of two automata is a refinement of the base automaton (\(a\mbrk{b} \leq a\)) in restricted interesting cases.
-% TODO: probably remove, this is was written when the previous section was not yet written
-\Ludo{lost}{I do not understand the last sentence}
-Hopefully they can be used as simpler (and less expensive) versions of the real refinement relation in the case the manipulated automata respect some constraints.
+The main goal of this section is to explain the different aspects of refinement in restricted cases so that they are not all introduced at once in the real refinement relation.
+In particular if we have a family of open automata \(A_i \defobject \OA{S_i}{s_{0i}}{J_i}{V_i}{\sigma_{0i}}{T_i}\), \(i \in \mdbrk{0; n}\), let \(A \defobject \OA{S}{s_0}{J}{V}{\sigma_0}{T}\) be such that \(A = A_0\psubst{j_i \mapsto A_i \middle| i \in \mdbrk{1; n}}\).
+Recall that there is no relation between the holes of \(A\) and \(A_0\) because \(J = \mpar{J_0 \uplus \biguplus_{i \in \mdbrk{1; n}} J_i} \setminus \mset{j_i}{i \in \mdbrk{1; n}}\) is neither subset nor superset of \(J_0\).
+So looking at restricted cases where holes are related in a specific manner can help understanding the general case.
+Hopefully the intermediate refinement relation introduced can be used as simpler (and less expensive to compute) versions of the real refinement relation in the case the manipulated automata respect some constraints.
 
-Composing an open automaton can give an automaton where the holes of the obtained automatonn cannot be relatd with the holes of the original one.
-So looking at restricted cases where holes are related in a specific manner can help understanding the general case.
+In the following definitions, \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) are two open automata.
 
-For two open automata \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), we first define a refinement relation where holes of the compared automata are identical.
-This relation is the basis for all the other ones.
-The goal is to characterise open automata that have a more determined (more deterministic) behaviour without adding deadlocks.
-This corresponds to ???? in the classical definitions of refinement \Ludo{TODO}{j imagine que rabea peut donner des refs ici}.
-\begin{defi}[Hole-identical refinement] % TODO: transition variables
-If \(J_1 = J_2\) then ``\(A_1\) is a hole-identical refinement of \(A_2\)", noted \(A_1 \leq_= A_2\), is defined as:
-\[ \exists R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2], \sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}} \qwedge R \text{ hole-identical simulation of } A_1 \text{ in } A_2 \]
-\end{defi}
-As in other simulation-like relations, \(R\) is a witness of \(A_1 \leq_= A_2\).
-The standard requirements for (bi)simulations are that \(R\) relates initial states, transitions can be matched, and target of matched transitions with related sources are also related.
-For a bisimulation transitions are matched one-to-many from each automaton to the other, but for a simulation only one way is used.
-The definition above requires explicitely that initial states are related, the other requirement are encapsulated in the definition (below) of hole-identical simulation.
-
-The specificities of open automata at on the relation between the (initial) states.
-\Ludo{lost}{When reading the next sentences I am not sure where we are going, what is notation introduction of concepts or definitions, please clarify}
-The relation \(R\) relates \(i_1\) to \(i_2\) under the condition that the current value of variables satisfies \(R\mpar{i_1, i_2}\).
-If two states \(s_1 \in S_1, s_2 \in S_2\) are not(/never) related then \(\nvdash R\mpar{s_1, s_2}\).
-The predicate \(R\mpar{s_{01}, s_{02}}\) is used to take into account the fact that a state is also constituted of the value of the variables.
-This is already used in FH-bisimulation introduced in previous articles about open automata.
-\Ludo{OK}{I guess I understand that you want to reach the next sentence as an explanation of the notations used in the definition, I mainly believe it is necessary to re-organise the ideas before}
-So the meaning of \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\) is that the initial states with the initial valuation are effectively related.
-% TODO: Also a relic of the past, when things were explained on the go instead of in a dedicated section.
-Remove if already explained, move otherwise
-\newpage % TODO: remove when less comments :)
-
+The following relation is the basis for all the other ones.
+We restrict the relation to automata with the same holes so that we can explain the refinements independant from composition.
+These refinements are ``specifying more initial variables" and ``adding determinism".
+This corresponds to the classical simulation refinement on LTS \Ludo{TODO}{j imagine que rabea peut donner des refs ici}.
 \begin{defi}[Hole-identical simulation]
-\Quentin{``\(R\) is a hole-identical simulation of \(A_1\) in \(A_2\)"}{Any idea on how to note that?
-\(R \vDash A_1 \leq_= A_2\) for instance.} \Ludo{reply}{I believe the notation  \(R \vDash A_1 \leq_= A_2\) is not bad bbut for the text I would rather write a1 is a simulation of a2 according to (as witnessed by) R ???} is defined as: % TODO: Actually this was already answered, \wrel is the settled way
-\begin{multline*}
-	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \\
+\(R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]\) is a hole-identical simulation of \(A_1\) by \(A_2\) if:
+\defitem \(J_1 = J_2\);
+\defitem \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\);
+\defitem \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)\vspace{-8pt}
+\noindent\begin{multline*}
 	\mpar{\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{} \in \fOT{s_2}}^{x \in X}, \\[12pt]
-		\forall \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\
-		\quad \sigma \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_{j \in J'} \beta_{1j} = \beta_{2xj} \\[12pt]
+		\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
+		\quad \mpar{\forall x \in X, J'_{2x} \subseteq J'_1} \\ % TODO: or = ?
+		\quad \wedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_{j \in J'_{2x}} \beta_{1j} = \beta_{2xj} \\[12pt]
 			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
@@
 	\end{array}} \\
-	\wedge \forall \sigma: \mpar{V_1 \uplus V_2} \to \values, \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
+	\wedge V_1 \uplus V_2 \uplus \biguplus_{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
 \end{multline*}
 \end{defi}
-The first two lines quantify on source states, transitions (and target states) and source states valuations.
-The \Ludo{3\textsuperscript{rd}}{is this the good line number?} line is the condition to ensure that transitions are not matched to incompatible ones:
-For all variable assignments of the two automata and all hole actions (quantification of \(\sigma\)), assuming that the states were related and the transition in \(A_1\) is possible (\(R\mpar{s_1, s_2} \wedge g_1\) part) then there is always a set of transitions, not necessarily only one as several transitions might simulate the same one depending on the value of variables for example; these transitions can be performed (\(g_{2x}\)), produce the same action (\(\alpha_1 = \alpha_{2x}\)), accept the same action from the holes (\(\beta_{1j} = \beta_{2xj}\)) and satisfy the predicate for relating the target states after variable update (\(R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\)).
+The hole-identical name is referring to the first part of the definition: holes indices are the same in related automata.
+The third item of the definition has two parts:
+The first part is the main requirement, a (not equivalent) reordering of the pre-simulation requirement so that it better fits SMT.
+Instead of matching an effective transition to another effective transition as in the pre-simulation definition, we match an open transition to a family of covering open-transitions.
+On top of that the holes involved in the family of transition can vary and only be a subset of the transition simulated.
+We can force their equality (between all the \(J'\), not only the \(J'_{2x}\) because of transitivity issues), and get a perfectly valid alternative depending on the properties you expect from the refinement relation.
+The subset version is strange in term of simulation since a hole can perform more actions in a simulated run.
+The second part is directly the deadlock reduction requirement.
 
-The notion of refinement here is stating that \(A_1\) is a refinement of \(A_2\) if \(A_1\) can be simulated \Ludo{in}{by?} \(A_2\).
-The hole-identical part is referring to the fact that holes indices are the same and identical holes indices have to perform the same actions.
-On top of that the last line ensures that no deadlock is introduced.
-It can be interpreted ``assuming the predicate holds and there is any possible transition in \(A_2\) (= no deadlock), then there must be a possible transition in \(A_1\) (= no deadlock)''.
-It does not have to ensure that this transition isn't garbage or that the target states are related because the first part of the simulation already does it.
-Also if there was a deadlock then there is no transition because no transition can be simulated in a deadlock.
-In that regard deadlock reduction caracterises in fact the absence of deadlock creation.\Ludo{?}{the last sentence is not very clear}
+\begin{exi}
+\begin{figure}
+\centering
+\input{parallel_comp.tex}
+\vrule
+\input{n_control_switch.tex}
+\caption{On the left: Parallel composition operator; On the right: n control switches automaton}
+\label{fig:hisim}
+\end{figure}
+To illustrate the definition and the different refinement operations, Figure \ref{fig:hisim} introduces two related open automata with same holes \(\mbrc{l, r}\).
+The automaton on the left is a parallel composition: any hole can perform actions at any time, the actions are passed unmodified and no synchronisation is performed.
+The automaton on the right is a sequential composition with \(n\) control switches: a hole performs a sequence of actions then the other does, there are \(n\) seqences of a single automaton doing actions without the other performing some.
+The initial valuation of the right automaton is in blue, actually we want to consider both the automaton with this initial valuation and the one without.
 
-\begin{exi} % TODO
+Intuitively the right automaton is a refinement of the left automaton because the left automaton is what happens when there was no bound \(n\) in the right automaton.
+Also the right automaton with the initial valuation is a refinement of the right automaton with the initial valuation because a ``\(1\) control switches" is an instance of a ``\(n\) control switches".
+
+First let consider \(R\), a hole-identical simulation of \(n\) control switches by parallel composition:
+\[ R \defobject \mbrc{\mpar{l, ||} \mapsto \top, \mpar{r, ||} \mapsto \top} \]
+
 \end{exi}
 
-\begin{lem}[Equivalent definition]
+% TODO: re-écriture
+\begin{lem}[Hole-identical simulation is a pre-simulation]
 \begin{gather*}
@@
 \end{array}} \\
-\iff \\
+\implies \\
 \mpar{\everymath{\displaystyle}\begin{array}{l}
@@
 \begin{multline}
-	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \uplus \bigcup_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values, \\
+	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values, \\
 	\sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \tag{WD}\label{eq:drWD}
@@
 	\[ \sigma \uplus \nu \vdash \fguard{t_2} \hyp{2'} \]
-	\(R\) satisfies \eqref{eq:drWD} with the current value of \(\mpar{s_1, s_2}\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \(\bigcup_{t_2 \in \fOT{s_2}} \fguard{t_2}\) so we have:
+	\(R\) satisfies \eqref{eq:drWD} with the current value of \(\mpar{s_1, s_2}\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \(\biguplus_{t_2 \in \fOT{s_2}} \fguard{t_2}\) so we have:
 	\[ \sigma \uplus \nu \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{3} \]
-	The \(\vdash\) hides an implicit \(\exists\) that we use to get values to the variables in \(\bigcup_{t_1 \in \fOT{s_1}}\) in a valuation \(\mu\).
+	The \(\vdash\) hides an implicit \(\exists\) that we use to get values to the variables in \(\biguplus_{t_1 \in \fOT{s_1}}\) in a valuation \(\mu\).
 	The left side of the implication is proved using \hyp{1} and \hyp{2'} for the branch \(t_2\) of the disjunction.
@@
 \item[\(\eqref{eq:drWD}\Leftarrow\eqref{eq:drID}\):]
-	Let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \(\sigma: V_1 \uplus V_2 \uplus \bigcup_{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values\).
+	Let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \(\sigma: V_1 \uplus V_2 \uplus \biguplus_{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values\).
 	We want to prove:
@@
 We want to prove
-\[ \forall s \defobject \mpar{s_p, s_c} \in S, \forall \sigma: V \uplus \bigcup_\subbox{t_p \in \fOT{s_p}} \fvars{t_p} \to \values, \sigma \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \tag{WD}\label{eq:nlcWD} \]
+\[ \forall s \defobject \mpar{s_p, s_c} \in S, \forall \sigma: V \uplus \biguplus_\subbox{t_p \in \fOT{s_p}} \fvars{t_p} \to \values, \sigma \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \tag{WD}\label{eq:nlcWD} \]
 \[ \iff \]
@@
 	\[ \sigma \uplus \nu \vdash \fguard{t_p} \hyp{2'} \]
-	\(R\) satisfies \eqref{eq:nlcWD} with the current value of \(s\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \(\bigcup_{t_p \in \fOT{s_p}} \fguard{t_p}\) so we have:
+	\(R\) satisfies \eqref{eq:nlcWD} with the current value of \(s\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \(\biguplus_{t_p \in \fOT{s_p}} \fguard{t_p}\) so we have:
 	\[ \sigma \uplus \nu \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{3} \]
-	The \(\vdash\) hides an implicit \(\exists\) that we use to get values to the variables in \(\bigcup_{t \in \fOT{s}}\) in a valuation \(\mu\).
+	The \(\vdash\) hides an implicit \(\exists\) that we use to get values to the variables in \(\biguplus_{t \in \fOT{s}}\) in a valuation \(\mu\).
 	The left side of the implication is proved using \hyp{1} and \hyp{2'} for the branch \(t_p\) of the disjunction.
@@
 \item[\(\eqref{eq:nlcWD}\Leftarrow\eqref{eq:nlcID}\):]
-	Let \(s \defobject \mpar{s_p, s_c} \in S\), \(\sigma \in V \uplus \bigcup_{t_p \in \fOT{s_p}} \fvars{t_p} \to \values\).
+	Let \(s \defobject \mpar{s_p, s_c} \in S\), \(\sigma \in V \uplus \biguplus_{t_p \in \fOT{s_p}} \fvars{t_p} \to \values\).
 	We want to prove:

### 2021-05-27 2021-Refinement/report.tex
Section 6 cleaned

@@
 
-% possible examples for refinement: + <= |, ; <= |
 % transitions between sections
 % TODO: CITER LES CONFERENCES
-% Proof sketch
 
@@
 The contributions of this article are the definition of composition for open automata without having to define open pNets, and the introduciton of several refinement relations for open automata\marginpar{TODO: expand}.
+
+% Related work: thesis
 
@@
 \begin{defi}[Open automaton]
-A open automaton is a tuple \(\OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(S\) the set of states, \(s_0 \in S\) the initial state, \(V\) the set of variable names unique to this automaton, \(\sigma_0: V' \to \values\) the initial valuation of variables where \(V' \subseteq V\), \(J\) the set of hole names and \(T\) the set of open transitions.
+A open automaton is a tuple \(\OAg\) with \(S\) the set of states, \(s_0 \in S\) the initial state, \(V\) the set of variable names unique to this automaton, \(\sigma_0: V' \to \values\) the initial valuation of variables where \(V' \subseteq V\), \(J\) the set of hole names and \(T\) the set of open transitions.
+A pair of a state and a valuation is called a configuration.
 
@@
 The intuition of an open automaton is a partially defined LTS with variables, guards on transitions and parametrised actions.
-Initially the automaton is in the initial state with the initial valuation.
-In any state with any valuation, it can perform effective transitions which source state is the current state and which guard is satisfiable in the current valuation if the holes emit the indicated actions.
+Initially the automaton is in the initial state with an extension on all the variables of the initial valuation.
+In any configuration, it can perform effective transitions which source state is the current state and which guard is satisfiable in the current valuation if the holes emit the indicated actions.
 An effective transition is a transition where every variable that is not an automaton variable is instanciated with a value.
-By performing the effective transition, the automaton emits the indicated action and updates its variables and state according to the target state and variables assignements.
+By performing the effective transition, the automaton emits the indicated action and updates its configuration according to the target state and variables assignements.
 
@@
 \begin{exi}[Enable, variable-oriented]
-The automaton drawn on the right side of Figure \ref{fig:enable} is \(\OA{\mbrc{\_}}{\_}{\mbrc{v}}{l^\mbrc{v}}{\mbrc{l, r}}{T}\) where transitions in \(T\) are:
+The automaton drawn on the right side of Figure \ref{fig:enable} is \(\OA{\mbrc{»}}{»}{\mbrc{v}}{v \mapsto l}{\mbrc{l, r}}{T}\) where transitions in \(T\) are:
 \begin{align*}
-	\OT{\_}{\_}{x}{\mbrc{l \mapsto x}}{v = l \wedge x \neq \delta}{\mbrc{}} &&
-	\OT{\_}{\_}{\tau}{\mbrc{l \mapsto \delta\mpar{x}, r \mapsto \act{acc}\mpar{y}}}{v = l \wedge x = y}{\mbrc{v \gets r}} &&
-	\OT{\_}{\_}{x}{\mbrc{r \mapsto x}}{v = r}{\mbrc{}}
+	\OT{»}{»}{x}{\mbrc{l \mapsto x}}{v = l \wedge x \neq \delta}{\mbrc{}} &&
+	\OT{»}{»}{\tau}{\mbrc{l \mapsto \delta\mpar{x}, r \mapsto \act{acc}\mpar{y}}}{v = l \wedge x = y}{\mbrc{v \gets r}} &&
+	\OT{»}{»}{x}{\mbrc{r \mapsto x}}{v = r}{\mbrc{}}
 \end{align*}
@@
 In a run, when taking effective transitions (without local variables), its value is not substituted with a closed term.
-For instance \nmm{\OT{\_}{\_}{\tau}{\mbrc{l \mapsto \tau}}{v = l \wedge \tau \neq \delta}{\mbrc{}}} is an effective transition generated from the second transition but not \nmm{\OT{\_}{\_}{\tau}{\mbrc{l \mapsto \tau}}{l = l \wedge \tau \neq \delta}{\mbrc{}}} (result of the forbidden substitution \(v \mapsto l\)).
+For instance \nmm{\OT{»}{»}{\tau}{\mbrc{l \mapsto \tau}}{v = l \wedge \tau \neq \delta}{\mbrc{}}} is an effective transition generated from the second transition but not \nmm{\OT{»}{»}{\tau}{\mbrc{l \mapsto \tau}}{l = l \wedge \tau \neq \delta}{\mbrc{}}} (result of the forbidden substitution \(v \mapsto l\)).
 
@@
 \section{Composition of Open Automata}\label{sec:comp}
+% TODO: distinguish composition from "parallel composition (pure interleaving)"
 Open automata are partially specified automata, part of that partiality comes from the holes.
@@
 \begin{defi}[Composition of open automata]
-The composition of \(A_c \defobject \OA{S_c}{s_{0c}}{V_c}{\sigma_{0c}}{J_c}{T_c}\) in the hole \(k \in J_p\) of \(A_p \defobject \OA{S_p}{s_{0p}}{V_p}{\sigma_{0p}}{J_p}{T_p}\) is
+The composition of \(A_c \defobject \OAg[c]\) in the hole \(k \in J_p\) of \(A_p \defobject \OAg[p]\) is
 \begin{align*}
@@
 	A_1\subst{A_2}{j}\subst{A_3}{j'} & = A_1\subst{A_3}{j'}\subst{A_2}{j} & j, j' & \in J_1 \\
-	A_1\subst{A_2}{j_1}\subst{A_3}{j_2} & = A_1\subst{A_2\subst{A_3}{j_2}}{j_1} & \mpar{j_1, j_2} & \in J_1 \times J_2
+	\mpar{A_1\subst{A_2}{j_1}}\subst{A_3}{j_2} & = A_1\subst{A_2\subst{A_3}{j_2}}{j_1} & \mpar{j_1, j_2} & \in J_1 \times J_2
 \end{align*}
@@
 \end{prop}
-This propriety is induced by the composition on open pNets. % LATER: proof?
+This property is induced by the composition on open pNets.
 Intuitively it holds because the cartesian product of states, the union of sets, the union of maps and the conjunction on formulas (in the guards) are commutative and associative.
-This allows us to define the parallel composition \(A\psubst{A_j^{j \in J'}}\) if there is any order of (sequential) composition where each \(A_j\) is composed in the hole \(j\).
+This allows us to define the parallel composition \(A\psubst{A_j^{j \in J'}}\) as the result of any order of (sequential) composition where each \(A_j\) is composed in the hole \(j\).
+% OR pcomp [[j |-> A_j]]
 
 \section{Properties of a refinement relation for Open Automata}\label{sec:proofelts}
-There are several properties we may want from a refinement relation.
+There are several properties we may expect from a refinement relation.
 Depending on these properties, different kinds of refinement can be used.
@@
 
-Informally, a simulation relation relating two automata means that one automaton states and transitions can be simulated by the other automaton.
+Informally, a simulation relating two automata means that every run of one automaton can be simulated by the other.
 Simulations are defined by relating states of automata.
@@
 
-Note that here there are two relations:
-The first is between states of two specific automata (\(R \subseteq S_1 \times S_2\)), the second is between automatas (\(A_1 \leq A_2\)).
+Note that in the previous paragraph there are two relations:
+The first is between states of two specific automata (\(R \subseteq S_1 \times S_2\)), the second is between automata (\(A_1 \leq A_2\)).
 Generally the second is implicit because its definition is always \(\exists R \subseteq S_1 \times S_2, P\mpar{R}\) with \(P\) a property, and only talking about \(R\) and \(P\) is sufficient.
 However later on in this article we will define more complex relations on automata so we clarify the distinction now.
-A relation of second kind will be called ``relation on automata" whereas a relation of the first kind could be called ``relation on states" though valuations also play the same role as states.
+A relation of second kind will be called ``relation on automata" whereas a relation of the first kind is called ``relation on configurations" as defined below.
 In the work on FH-bisimulation\marginpar{re-cite FH-bisim as near as the previous citation?} such a relation \(R\) was defined as triples in \(S_1 \times S_2 \times \formulas\) where for \(\mpar{s_1, s_2} \in S_1 \times S_2\) there is a unique \(f \in \formulas\) such that \(\mpar{s_1, s_2, f} \in R\).
 This is classically the definition of a function from \(S_1 \times S_2\) to \(\formulas\) so we will define it as such.
-\begin{defi}[Relation under predicate]
-A relation under predicate between states of two automata \(\OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(\OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) is a function \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
+\begin{defi}[Relation on configurations]
+A relation on configurations of two open automata \(\OAg[1]\) and \(\OAg[2]\) is a function \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
 
@@
 \end{defi}
-For a relation on automata \(\wrel{}{}{}\) which uses a relation under predicate to state that two element are related \(\forall x \, x', \wrel{x}{x'}{} \iff \exists R, P\mpar{R}\), there is no unicity on \(R\).
-To specify which witness is used in \(\wrel{x}{x'}{}\), we note \(\wrel{x}{x'}{R}\) where \(R\) is that witness.
 
@@
 \defitem \textbf{a preorder} iff it is reflexive and transitive;
-\defitem \textbf{correct w.r.t.\@ composition} iff \(\forall a\, b, a\mbrk{b} \leq a\);
-\defitem \textbf{complete w.r.t.\@ composition} iff \(\forall a\, b, a \leq b \implies \exists c, a \cong b\mbrk{c}\);
-\defitem \textbf{context refining for composition} iff \(\forall a\, b\, c, a \leq b \implies a\mbrk{c} \leq b\mbrk{c}\);
-\defitem \textbf{congruent for composition} iff \(\forall a\, b\, c, a \leq b \implies c\mbrk{a} \leq c\mbrk{b}\);
-\defitem \textbf{compatible with composition} iff \(\forall a\, b\, c\, d, a \leq b \wedge c \leq d \implies c\mbrk{a} \leq d\mbrk{b}\);
+\defitem \textbf{correct w.r.t.\@ composition} iff \(\forall a\, b, a\subst{b}{j} \leq a\);
+\defitem \textbf{complete w.r.t.\@ composition} iff \(\forall a\, b, a \leq b \implies \exists c, a \cong b\subst{c}{j}\);
+\defitem \textbf{context refining for composition} iff \(\forall a\, b\, c, a \leq b \implies a\subst{c}{j} \leq b\subst{c}{j}\);
+\defitem \textbf{congruent for composition} iff \(\forall a\, b\, c, a \leq b \implies c\subst{a}{j} \leq c\subst{b}{j}\);
+\defitem \textbf{compatible with composition} iff \(\forall a\, b\, c\, d, a \leq b \wedge c \leq d \implies c\subst{a}{j} \leq d\subst{b}{j}\);
 \defitem \textbf{compatible with FH-bisimulation} iff \(\forall a\, b\, c, d, a \cong b \wedge c \cong d \wedge a \leq c \implies b \leq d\).
@@
 Correctness w.r.t.\@ composition means that every composition is considered a refinement.
-This property captures the expectated behaviour of a refinement relation on a compositionnal structure like the open automata.
-Completeness w.r.t.\@ composition means that a refinement correspond to the left automaton being equivalent to some composition of the right automaton.
-This property is useful if we want to caracterise the kind of operations that can generate any refined automaton starting from the specification.
+This property captures the expected behaviour of a refinement relation on a compositionnal structure like the open automata.
+Completeness w.r.t.\@ composition means that a refinement corresponds to the left automaton being equivalent to some composition of the right automaton.
+This property is useful if we want to characterise the kind of operations that can generate any refined automaton starting from the specification.
 We won't have it because extending the domain of the initial valuation will be a refinement which can't be expressed with composition.
@@
 Compatibility with composition is the conjunction of the two latter (assuming the relation is a preorder).
-This property is a must have on compositionnal structures to be of any use in verification, proofs and for model checking.
+This property is required on compositionnal structures to be of any use in verification, proofs and for model checking.
 Finally compatibility with FH-bisimulation is the refinement not being able to distinguish two FH-bisimilar automata.
@@
 The important properties we consider for the relation on states are being a simulation and the reduction of deadlocks as defined in the following definitions.
-\begin{defi}[Pre-simulation on open automata]
-\Quentin{}{Is the definition satisfying now?}
-For two automata \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), a relation under predicate \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a pre-simulation if it satisfies both
-\defitem Initial states are related under initial valuations: \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\);
+\begin{defi}[Pre-simulation]
+For two open automata \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\), a relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a pre-simulation if it satisfies both
+\defitem Initial configurations are related: \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\);
 \defitem From related states, all out-transitions from \(A_1\) can be simulated in \(A_2\) and their target states are related:
@@
 Apart from holes, this is a natural extension of the notion of simulation on LTS, which is the same definition without variables and holes and guards.
-The treatment of holes in the FH-bisimulation is that holes with the same name will receive the same open automata when composed and the resulting open automata will still be equivalent.
+In FH-bisimulation, holes with the same name will receive the same open automaton when composed, and the resulting open automaton will still be equivalent.
 Here we assume that one of the related open automata can be obtained by composing an open automaton in a hole, open automaton which can have holes itself.
-This implies that there is no relation between their holes, \(J = \mpar{J_p \uplus \biguplus_{i \in \mdbrk{1; n}} J_i} \setminus \mset{k_i}{i \in \mdbrk{1; n}} \) is neither subset nor superset of \(J_p\).
+This implies that there is no relation between their holes, for instance composing \(A_i, 1 \leq i \leq n\) in \(A_0\) gives the holes \(J \defobject \mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{k_i}{1 \leq i \leq n} \) that is neither subset nor superset of \(J_0\).
 Yet we still assume that in holes with the same name, the same open automaton will be composed.
@@
 
-Deadlocks are states and valuations that are reachable in a run and from which no further transition is possible.
+Deadlocks are configurations reachable in a run and from which no further transition is possible.
 They can arise unpredictably when parallelism is involved (which is the case in our composition) and they break the intended behaviour of a system.
@@
 \begin{defi}[Deadlock reduction, intuitive definition]
-A relation under predicate \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if:
+A relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if:
 \defitem It is a pre-simulation;
@@
 
-In all these properties, ``Deadlock reduction" conflicts with ``composition correctness" by disallowing some unwanted cases where an automaton in a hole cannot produce any action that any out-transition expects.
+``Deadlock reduction" conflicts with all the properties where composition is involved (for instance ``composition correctness") by disallowing some unwanted cases where an automaton in a hole cannot produce any action that any out-transition expects.
 In particular filling a hole with the deadlock automaton (only one state without out-transitions) is not considered a refinement for a deadlock reducing relation.
-A way to solve this conflict is to characterise a composition that do not introduce deadlocks, which will be used instead of the composition introduced earlier.
+A way to solve these conflicts is to characterise a composition that do not introduce deadlocks, which will be used instead of the composition introduced earlier.
 \begin{defi}[Reachability]
-For any open automata \(A \defobject \OA{S}{s_0}{V}{\sigma_0}{J}{T}\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is a predicate on states such that
-\defitem \(\sigma_0 \vdash \reach{A}\mpar{s_0}\).
-\defitem \nmm{\bigsymb{\forall} t \defobject \OTg \in T, \forall \nu: \fvars{t} \to \values, \nu \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}}.
+For any open automata \(A \defobject \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is a predicate on states such that
+\defitem \(\sigma_0 \vdash \reach{A}\mpar{s_0}\)
+\defitem \nmm{\bigsymb{\forall} t \defobject \OTg \in T, \forall \nu: \fvars{t} \to \values, \nu \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}}
 \end{defi}
@@
 The reachability predicate is used to characterise the states and valuations that are reachable in a run of an automaton.
-In fact the role of the predicate is to characterise potentially reachable configurations without having to characterise the fact that the state and valuation are the result of a valid path in an automaton.
+In fact the role of the predicate is to characterise potentially reachable configurations without having to characterise configurations as the result of a valid path in an automaton.
 
-To do that we impose that the initial state is reachable in the initial valuation and that reachability is preserved by taking valid transitions.
+To do that we impose that the initial configuration is reachable and that reachability is preserved by taking valid transitions.
 This effectively makes reachability account for all paths and potentially over-approximate the reachable configurations.
@@
 \begin{align*}
-	f\mpar{p} = \mbrc{s' \mapsto p\mpar{s'} \vee \bigsymb{\bigvee_\subbox{\OTg \,\in\, \fIT{s'}}} p\mpar{s}\psubst{\psi} \wedge g} &&
+	f\mpar{p} = \mbrc{\mbox{\nmm{s' \mapsto p\mpar{s'} \vee \bigsymb{\bigvee_\subbox{\OTg \,\in\, \fIT{s'}}} p\mpar{s}\psubst{\psi} \wedge g}}} && % TODO: fix that in some way
 	\sigma_0 \vdash \reach{A}\mpar{s_0} &&
@@
 \begin{defi}[Non-locking composition, intuitive definition]
-Let  \(A_p\subst{A_c}{k} = \OA{S}{s_0}{V}{\sigma_0}{J}{T}\) with \(A_c \defobject \OA{S_c}{s_{0c}}{V_c}{\sigma_{0c}}{J_c}{T_c}\), \(A_p \defobject \OA{S_p}{s_{0p}}{V_p}{\sigma_{0p}}{J_p}{T_p}\) and \(k \in J_p\).
-The composition is non-locking if there is a reachability predicate such that from reachable configurations, if there was a possible transition in \(A_p\) then there is a possible transition in \(A_p\subst{A_c}{k}\):
+Let \(A_p\subst{A_c}{j} = \OAg\) with \(A_c \defobject \OAg[c]\), \(A_p \defobject \OAg[p]\) and \(j \in J_p\).
+The composition is non-locking if there is a reachability predicate such that from reachable configurations, if there was a possible transition in \(A_p\) then there is a possible transition in \(A_p\subst{A_c}{j}\):
 \begin{multline*}
-	\forall s \defobject \mpar{s_p, s_c} \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A_p\subst{A_c}{k}}\mpar{s}} \implies \\
+	\forall s \defobject \mpar{s_p, s_c} \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A_p\subst{A_c}{j}}\mpar{s}} \implies \\
 	\mpar{\exists t_p \in \fOT{s_p}, \exists \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \vdash \fguard{t_p}} \implies \\
@@
 \begin{defi}[Deadlock reduction, working definition]
-A relation under predicate \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if it is a pre-simulation and:
+A relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if it is a pre-simulation and:
 \begin{multline*}
@@
 \end{defi}
-The requirement here is that from any configuration related configurations, if there is a possible transition in the second automaton (whatever the value of the free variables) then there is a possible transition in the first automaton (the existential quantifier is implicit in the notation \(\vdash\)).
-The transition are not matched because the relation under predicate is a pre-simulation and it is sufficient to ensure it as will be shown in the proof.
+The requirement here is that from any related configurations, if there is a possible transition in the second automaton (whatever the value of the free variables) then there is a possible transition in the first automaton (the existential quantifier is implicit in the notation \(\vdash\)).
+The transition are not matched because the relation on configurations is a pre-simulation and it is sufficient to ensure it as will be shown in the proof.
 Apart from the matching transitions this is exactly the same explaination as the intuitive definition.
@@
 \begin{defi}[Non-locking composition, working definition]
-The composition \(A \defobject A_p\subst{A_c}{k}\) is a non-locking composition if:
-\[ \forall ss \defobject \mpar{s_p, s_c} \in S, \forall \sigma: V \uplus \biguplus_\subbox{t_p \in \fOT{s_p}} \fvars{t_p} \to \values, \sigma \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
+The composition \(A \defobject A_p\subst{A_c}{j}\) is a non-locking composition if:
+\[ \forall s \defobject \mpar{s_p, s_c} \in S, \forall \sigma: V \uplus \biguplus_\subbox{t_p \in \fOT{s_p}} \fvars{t_p} \to \values, \sigma \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
 \end{defi}
@@
 It is not true.
-Actually even if the last composition is non-locking there is no guarantee that there is an order of sequential composition that is non-locking at every step.
+Actually even if the last composition of any order of composition is non-locking there is no guarantee that this order is non-locking at every step.
 However the oppsite way is true even if uninformative:
@@
 
-A relation on open automata and its corresponding relation under predicate are simulations if the latter is a deadlock reducing pre-simulations and the former is a preorder.
+A relation on open automata and its corresponding relation on configurations are simulations if the latter is a deadlock reducing pre-simulations and the former is a preorder.
 With all these properties we can now look at some concrete refinement relations.
 
-% Mettre des sets de noms en commun qu'on veut effectivement mapper pour la transitivité
-% J'2 \subseteq J'1 in hole-subset, J'1 \subseteq J'2 in hole-superset (decide of transition variable with holes); composition with new holes is hole-subset where hole variables are free then hole-superset where hole names have no conflicts with removed holes.
-Transitivity must ensure holes name have no conflict for that reason!
-\section{Refinement relations in restricted cases}\label{sec:prelref}
+\section{Refinement relations in restricted cases}\label{sec:prelref} % TODO: Fold definitions and proofs
 The main goal of this section is to explain the different aspects of refinement in restricted cases so that they are not all introduced at once in the real refinement relation.
-In particular if we have a family of open automata \(A_i \defobject \OA{S_i}{s_{0i}}{J_i}{V_i}{\sigma_{0i}}{T_i}\), \(i \in \mdbrk{0; n}\), let \(A \defobject \OA{S}{s_0}{J}{V}{\sigma_0}{T}\) be such that \(A = A_0\psubst{j_i \mapsto A_i \middle| i \in \mdbrk{1; n}}\).
-Recall that there is no relation between the holes of \(A\) and \(A_0\) because \(J = \mpar{J_0 \uplus \biguplus_{i \in \mdbrk{1; n}} J_i} \setminus \mset{j_i}{i \in \mdbrk{1; n}}\) is neither subset nor superset of \(J_0\).
+In particular if we have a family of open automata \(A_i \defobject \OAg[i]\), \(0 \leq i \leq n\), let \(A \defobject \OAg\) be such that \(A = A_0\psubst{j_i \mapsto A_i \middle| 1 \leq i \leq n}\).
+Recall that there is no relation between the holes of \(A\) and \(A_0\) because \(J = \mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{i \in \mdbrk{1; n}}\) is neither subset nor superset of \(J_0\).
 So looking at restricted cases where holes are related in a specific manner can help understanding the general case.
@@
 
-In the following definitions, \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) are two open automata.
-
-The following relation is the basis for all the other ones.
-We restrict the relation to automata with the same holes so that we can explain the refinements independant from composition.
-These refinements are ``specifying more initial variables" and ``adding determinism".
-This corresponds to the classical simulation refinement on LTS \Ludo{TODO}{j imagine que rabea peut donner des refs ici}.
-\begin{defi}[Hole-identical simulation]
-\(R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]\) is a hole-identical simulation of \(A_1\) by \(A_2\) if:
-\defitem \(J_1 = J_2\);
-\defitem \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\);
+We restrict the holes of the related automata so that we can explain the different refinements without their interactions.
+In the following definition, \(\triangle \in \mbrc{\subseteq, =, \supseteq}\).
+\begin{defi}[Hole-\(\triangle\) simulation]
+For two open automata \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\triangle\) simulation of \(A_1\) by \(A_2\) if:
+\defitem \(J_1 \triangle J_2\)
+\defitem \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
 \defitem \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)\vspace{-8pt}
@@
 		\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
-		\quad \mpar{\forall x \in X, J'_{2x} \subseteq J'_1} \\ % TODO: or = ?
+		\quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
 		\quad \wedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_{j \in J'_{2x}} \beta_{1j} = \beta_{2xj} \\[12pt]
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
 			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
@@
 	\end{array}} \\
-	\wedge V_1 \uplus V_2 \uplus \biguplus_{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
+	\wedge V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
 \end{multline*}
 \end{defi}
-The hole-identical name is referring to the first part of the definition: holes indices are the same in related automata.
 The third item of the definition has two parts:
@@
 Instead of matching an effective transition to another effective transition as in the pre-simulation definition, we match an open transition to a family of covering open-transitions.
-On top of that the holes involved in the family of transition can vary and only be a subset of the transition simulated.
-We can force their equality (between all the \(J'\), not only the \(J'_{2x}\) because of transitivity issues), and get a perfectly valid alternative depending on the properties you expect from the refinement relation.
-The subset version is strange in term of simulation since a hole can perform more actions in a simulated run.
 The second part is directly the deadlock reduction requirement.
 
-\begin{exi}
-\begin{figure}
-\centering
-\input{parallel_comp.tex}
-\vrule
-\input{n_control_switch.tex}
-\caption{On the left: Parallel composition operator; On the right: n control switches automaton}
-\label{fig:hisim}
-\end{figure}
-To illustrate the definition and the different refinement operations, Figure \ref{fig:hisim} introduces two related open automata with same holes \(\mbrc{l, r}\).
-The automaton on the left is a parallel composition: any hole can perform actions at any time, the actions are passed unmodified and no synchronisation is performed.
-The automaton on the right is a sequential composition with \(n\) control switches: a hole performs a sequence of actions then the other does, there are \(n\) seqences of a single automaton doing actions without the other performing some.
-The initial valuation of the right automaton is in blue, actually we want to consider both the automaton with this initial valuation and the one without.
+% TODO: expand on first part, especially the impact of /_\ on the different refinement allowed and what it means, and the fact that = could be substituted with \subseteq.
 
-Intuitively the right automaton is a refinement of the left automaton because the left automaton is what happens when there was no bound \(n\) in the right automaton.
-Also the right automaton with the initial valuation is a refinement of the right automaton with the initial valuation because a ``\(1\) control switches" is an instance of a ``\(n\) control switches".
-
-First let consider \(R\), a hole-identical simulation of \(n\) control switches by parallel composition:
-\[ R \defobject \mbrc{\mpar{l, ||} \mapsto \top, \mpar{r, ||} \mapsto \top} \]
-
-\end{exi}
-
-% TODO: re-écriture
-\begin{lem}[Hole-identical simulation is a pre-simulation]
-\begin{gather*}
+Examples of application of the different refinement relations are given in appendix \ref{apx:refrel}.
+\begin{thm} A hole-\(\triangle\) simulation is a pre-simulation. \end{thm}
+Let \(R\) be a relation on configurations.
+The condition \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\) is in both definitions so proving the following is sufficient:
+\begin{multline}
 	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \\
 	\mpar{\everymath{\displaystyle}\begin{array}{l}
-	\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{} \in \fOT{s_2}}^{x \in X}, \\[12pt]
-	\forall \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\
-	\quad \sigma \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-		\alpha_1 = \alpha_{2x} \wedge \bigwedge_{j \in J'} \beta_{1j} = \beta_{2xj} \\[12pt]
+		\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
+		\quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
+		\quad \wedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
 			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
 		\end{array}}
-\end{array}} \\
-\implies \\
-\mpar{\everymath{\displaystyle}\begin{array}{l}
-	\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\[6pt]
-	\quad \mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} \OTx{2}{}{2}{2} \in \fOT{s_2}, \\[12pt]
-	\qquad \sigma \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
-\end{array}}
+	\end{array}} \hyp{0}
+\end{multline}
+\[ \implies \]
+\begin{multline}
+	\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \forall \sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values, \\
+	\mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \\
+	\sigma \uplus \nu \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \goal{0}
+\end{multline}
+\begin{proof} Let \(\mpar{s_1, s_2} \in S_1 \times S_2\), \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}} and \(\sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values\) be such that
+\[ \sigma \vdash R\mpar{s_1, s_2} \wedge g_1 \hyp{1} \]
+In order to get the transition required to prove
+\begin{multline}
+	\bigsymb{\exists} t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \\
+	\sigma \uplus \nu \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \goal{0'}
+\end{multline}
+we use the hypothesis \hyp{0} with the transition \(t_1\) and get a family of transitions
+\[ \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X} \]
+such that the two following properties hold
+\begin{gather}
+	\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2 \hyp{2} \\
+	V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+		\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
+		\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+	\end{array}} \hyp{3}
+\end{gather}
+\hyp{3} holds for every values of the variables in \(V_1 \uplus V_2 \uplus \fvars{t_1}\) so in particular with the ones given by \(\sigma\).
+We gather the existential variables in a valuation:
+\begin{gather*}
+	\nu: \biguplus_{x \in X} \fvars{t_{2x}} \to \values \\
+	\sigma \uplus \nu \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \bigvee_{x \in X} \mpar{\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x}} \beta_{1j} = \beta_{2xj} \wedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \hyp{4}
 \end{gather*}
-\end{lem}
-The first property is one part of the hole-identical simulation, the second property is the central part of the \Ludo{refinement simulation requirement}{add reference to def (like "def x")}.
-If we prove the direct way of this equivalence and \(\leq_=\) is a preorder then \(\leq_=\) is a refinement simulation.
-The other way is there because I hope that it will be easier to use this formulation to prove that \(\leq_=\) is a preorder. % Will need to be modified
-\Ludo{One may wonder why it was not used}{rephrase and state in what sense this second one could be considered as better} in the definition if it is equivalent. % Informal!
-The reason is that the formulation used in definition??? is compatible with SMT solver, the place where it will most probably be used in practise.
-\begin{proof} Let \(\mpar{s_1, s_2} \in S_1 \times S_2\),
-\item[\(\implies\):] We admit the up formula as \(H_{def}\), let \(t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}\) and \(\sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values\) be such that \(H_{source} \defobject \sigma \vdash R\mpar{s_1, s_2} \wedge g_1\).
-	\(H_{def}\) applied to \(t_1\) gives \(\mpar{t_{2x} \defobject \OTx{2}{x}{2x}{1} \in \fOT{s_2}}^{x \in X}\) and the property \(H_{tmp}\) to which we give \(\sigma\) to get
-	\begin{multline*}
-		H_{smt} \defobject \sigma \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \\
-		\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_{j \in J'_1} \beta_{1j} = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}}
-	\end{multline*}
-	\Ludo{Unfolding the definition}{I really cannot understand this step you will need to explain us I believe, and add details here.
-TODOLudo: read the rest of the proof after explanation} of \(\sigma \vdash f\) where \(f\) is not a closed formula in \(H_{smt}\) gives an exists that we use to get \nmm{\nu: \biguplus_{x \in X} \fvars{t_{2x}} \to \values} and
-	\[ H_{valid} \defobject \sigma \uplus \nu \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-		\alpha_1 = \alpha_{2x} \wedge \bigwedge_{j \in J'_1} \beta_{1j} = \beta_{2xj} \\[12pt]
-		\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-	\end{array}} \]
-	\(R\mpar{s_1, s_2} \wedge g_1\) in \(H_{valid}\) does not depends on \(\nu\) so we can use \(H_{source}\) to prove it and get \(H_{cover}\).
-	\(H_{cover}\) is a disjunction that we can eliminate, action that gives a value \(x\) and
-	\[ H_{target}\mpar{x} \defobject \sigma \uplus \nu \vdash \alpha_1 = \alpha_{2x} \wedge \bigwedge_{j \in J'_1} \beta_{1j} = \beta_{2xj} \wedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \]
-	Now that we have a specific \(x\) we can say that in the bottom formula \(t_{2x}\) is a witness in \(T_2\).
-	By doing that, what we are left to prove is \nmm{\sigma \vdash \alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_1} \beta_{1j} = \beta_{2xj} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}}.
-	As a valuation for variables in \(\fvars{t_{2x}}\) we have \(\nu\), so \(H_{target}\mpar{x}\) concludes the proof.
-\item[\(\impliedby\):] We admit the bottom formula as \(H_{ref}\), let \(t_1 \defobject \OTx{1}{}{1}{} \in T_1\) % TODO; quantify on all valuations to get t_{2\sigma}
+The left side of the implication is proven by \hyp{1}, and we destruct the disjuntion on the right side to get \(x \in X\) and the hypothesis
+\[ \sigma \uplus \nu \vdash \alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \wedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \hyp{4'} \]
+We have \(J'_{2x} \cap J_1 \subseteq J'_{2x}\) and by \hyp{2}, \(J'_{2x} \cap J_1 = J'_1 \cap J_2 \subseteq J'_1\) so \(J'_{2x} \cap J_1 \subseteq J'_{2x} \cap J'_1\).
+Also \(J'_{2x} \cap J'_1 \subseteq J'_{2x} \cap J_1\) because \(J'_1 \subseteq J_1\) by definition of an open transition.
+Hence \(J'_{2x} \cap J_1 = J'_{2x} \cap J'_1\) in \hyp{4'}.
+We can get back to prove \goal{0'} with the transition \(t_{2x}\) and the valuation \(\nu\) by \hyp{4'}.
 \end{proof}
 
-\begin{thm} The hole-identical refinement relation is a preorder. \end{thm}
-\begin{proof}
-\item \emph{Reflexivity:} Let \(A\) be an open automaton with variables in \(V\).
-	The automaton variables on the right hand side of the relation will be noted \(v'\) for the equivalent variable \(v \in V\) in the automaton on the left hand side.
-	The simulation \nmm{R = \mset{\mpar{s, s} \mapsto \bigwedge_{v \in V} v = v'}{s \in S_1}} is a witness of \(A \leq A\).
-	Checking it is a simple exercise left to the reader in order to understand how the definition works.
-\item \emph{Transitivity:} Let \(A_1, A_2, A_3\) be open automata with respectively variables in \(V_1, V_2, V_3\) and states \(S_1, S_2, S_3\).
-	And let \(R_{12}\) be a witness of \(A_1 \leq_= A_2\) and \(R_{23}\) be a witness of \(A_2 \leq_= A_3\).
-	\[ R_{13}\mpar{s_1, s_3} \defobject \exists V_2, \bigvee_{s_2 \in S_2} R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \]
+\begin{thm} The hole-\(\triangle\) simulation on automata is a preorder. \end{thm}
+Reflexivity is immediate with \(R \defobject \mpar{s, s'} \mapsto \choice{\bigwedge_{v \in V} v_1 = v_2 & s = s'\\ \bot & s \neq s'}\) where \(v_x\) is the renaming to distinguish conflicting automaton variables.
 
-	Now let's prove that \(R_{13}\) is a witness of \(A_1 \leq_= A_3\):
-	\begin{itemize}
-	\item % TODO
-	\end{itemize}
-\end{proof}
-% TODO Properties: do not forget to add deadlock equivalence in the 3 theorems
-\begin{thm}[Hole-identical refinement correction]
-% TODO: Préordre, action-refinement possible, pas de nouveau deadlock, pas de nouveau livelock, chaque état (accessible) a son correspondant (simulation)
-\end{thm}
-\begin{proof}
-\end{proof}
-
-The goal of the following relation is to capture the case where holes are filled with automata that do not have any hole.
-It is supposed to be a relation for which filling holes with fully specified automata is a considered refinement.
-\begin{defi}[Hole-subset refinement]
-If \(J_1 \subseteq J_2\) then ``\(A_1\) is a hole-subset refinement of \(A_2\)", noted \(A_1 \leq_\subseteq A_2\) is defined as:
-\[ \exists R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2], \sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}} \wedge R \text{ hole-subset simulation of } A_1 \text{ in } A_2 \]
-\end{defi}
-This definitions is essentially the same as the hole-identical one excepted the constraint on holes which has been softened.
-
-\begin{defi}[Hole-subset simulation]
-``\(R\) is a hole-subset simulation of \(A_1\) in \(A_2\)" is defined as:
-\begin{multline*}
-	\forall s_1 \in S_1, s_2 \in S_2, \\
-	\mpar{\renewcommand\arraystretch{1.4}\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
-		\mpar{\forall x \in X, J'_1 = J'_{2x} \cap J_1} \wedge \forall \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\
-		\quad \sigma \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_{j \in J'_1} \beta_{1j} = \beta_{2xj} \\
-			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}} \\
-	\end{array}} \\
-	\wedge \forall \sigma: \mpar{V_1 \uplus V_2} \to \values, \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_2}
-\end{multline*}
-\end{defi}
-The difference with the hole-identical simulation is that the holes involved in the matched transitions don't have to be exactly the same anymore.
-The new constraint is that the holes in common (that is \(J'_1\)) should be involved at the same time and their action have to match.
-What happens on the other holes is unspecified except for the fact that, by being free variables they still need to be valued such that the transition is possible.
-
-\begin{exi} % TODO: Traffic light example
-\end{exi}
-
-An alternative version of this definition could enforce \(\exists J'_2 \subseteq J_2, \forall x \in X, J'_{2x} = J'_2\).
-Let's call it the alternative hole-subset simulation.
-This version would mean that the holes involved in every matched transitions must be the same.
-While this may seem more natural this leads to the unwanted behaviour that an automaton FH-bisimilar to a refinement of some specification might not be a refinement of that specification:
-\begin{prop}[Alternative hole-subset simulation is not compatible with FH-bisimulation]
-TODO: collapse a transition that was differenciated by having one filled hole involved and it should be simple
-\end{prop}
-This is a sufficient reason to discard this version although it seems more natural.
-\begin{prop}[Hole-subset refinement is compatible with FH-bisimulation]
-% TODO
-\end{prop}
-
-% Hole-subset refinement can be used to specify behaviour/constraints on holes (like an API: first do anything not involving the api, then initialise the api, then do whatever you want that do not unload the api, then unload the api by returning to the first state), then have a relation for every hole with a different automata and this means well behaving with respect to the environement (holes)
-\begin{exi} % TODO
-\end{exi}
-
-\begin{prop}[Hole-subset refinement is an extension of hole-identical refinement]
-Hole-subset refinement and hole-identical match when holes are identical.
-\end{prop}
-\begin{proof}
-When \(J_1 = J_2\), \(J'_1 = J'_{2x} \cap J_1 \iff J'_1 = J'_{2x} \cap J_2 \iff J'_1 = J'_{2x}\), which is the implicit constraint on hole actions in the hole-identical simulation.
-By that rewriting their definition match.
-\end{proof}
-Let's assume that this relation is also correct, the proof of correctness is given later for a more general refinement relation.
-\begin{thm}[Composition is a refinement]
-% TODO: Proof that filling holes with a fully specified automaton is a refinement
-\end{thm}
-\begin{proof}
-\end{proof}
+For three open automata \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\), such that \(R_{12}\) is a hole-\(\triangle\) simulation of \(A_1\) by \(A_2\) and \(R_{23}\) of \(A_2\) by \(A_3\), we want to define \(R_{13}\) by saying that there exists a state \(s_2 \in S_2\) and values for \(V_2\) such that \(R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}\).
+However we cannot talk about states in formulas.
+The solution is to expand the existential quantifier as we did in deadlock reduction, which is possible because states are finite.
+\nmm{R_{13} \defobject \mpar{s_1, s_3} \mapsto \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}} is a witness of the transitivity, proof is given in appendix \ref{apx:trans}.
 \begin{thm}[Context refinement]
@@
 \end{proof}
-\begin{thm}[Congruence with composition]
-% a <= b & c[a] <= c -> c[a] <= c[b]
-\end{thm}
+% Rédiger un paragraphe sur le fait que composer dans l'implem sans deadlock implique qu'il n'y a pas de deadlock quand on compose avec la spec, on voudrais avoirs l'autre sens mais ce n'est pas possible
+\begin{prop}[Composition correctness']
+% TODO: Proof that filling holes with a fully specified automaton is a refinement
+\end{prop}
 \begin{proof}
 \end{proof}
+\begin{prop}[Composition correctness"]
+% TODO: Proof that filling added holes with a fully specified automaton is a refinement
+\end{prop}
+\begin{proof}
+\end{proof}
+% J'2 \subseteq J'1 in hole-subset, J'1 \subseteq J'2 in hole-superset (decide of transition variable with holes); composition with new holes is hole-subset where hole variables are free then hole-superset where hole names have no conflicts with removed holes.
+Transitivity must ensure holes name have no conflict for that reason!
 
-% TODO: Give an example of what you want to capture BEFORE and after the relation
-The goal of the following relation is to capture the case where holes are filled with one hole automata.
-It is supposed to be a relation for which filling holes with one hole automata is a considered refinement.
-\begin{defi}[Hole-matching refinement]
-If \(\card{J_1} = \card{J_2}\) then ``\(A_1\) is a hole-matching refinement of \(A_2\)", noted \(A_1 \leq_\# A_2\) is defined as:
-\begin{multline*}
-	\exists R: \mpar{S_1 \times S_2} \to \formulas, \quad \exists f: J_1 \setminus J_2 \to J_2 \setminus J_1, \\
-	\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}} \qwedge f\mpar{J_1 \setminus J_2} = J_2 \setminus J_1 \\
-	\wedge R \text{ hole-f-matching simulation of } A_1 \text{ in } A_2
-\end{multline*}
-\end{defi}
-This definitions is essentially the same as the hole-identical except that the constraint on holes has been softened and it is compensated with a invertible map between non-shared holes.
-
-\begin{defi}[Hole-f-matching simulation]
-\(R\) is a hole-f-matching simulation of \(A_1\) in \(A_2\) is defined as:
-\begin{multline*}
-	\forall s_1 \in S_1, s_2 \in S_2, \\
-	\mpar{\renewcommand\arraystretch{1.4}\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
-		\mpar{\forall x \in X, J'_1 \cap J_2 = J'_{2x} \cap J_1 \wedge f\mpar{J'_1 \setminus J_2} \subseteq J'_{2x}} \wedge \forall \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\
-		\quad \sigma \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_1 \cap J_2} \beta_{1j} = \beta_{2xj} \\
-			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}} \\
-	\end{array}} \\
-	\wedge \forall \sigma: \mpar{V_1 \uplus V_2} \to \values, \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
-\end{multline*}
-\end{defi}
-% TODO: Matching a hole data with another hole is done with a_1=a_2x and constraint on respective variables, thus hole data is not uncontrained, same for action label because each transition has only 1 action label
-% TODO: Explain what happens on holes constraints and action constraints
-% J'_1x still necessary for the same reason essentially
-% f() subset J'1 \ J2 : equality is possible and give a valid alternative that must match each action with another action, even if the latter has no more the choice, basically the version given here allows to hide some choices from the hole
-
+% Mettre des sets de noms en commun qu'on veut effectivement mapper pour la transitivité
+% Explain what happens on holes constraints and action constraints
+% refinement can be used to specify behaviour/constraints on holes (like an API: first do anything not involving the api, then initialise the api, then do whatever you want that do not unload the api, then unload the api by returning to the first state), then have a relation for every hole with a different automata and this means well behaving with respect to the environement (holes)
 \section{Refinement relation for open automata}\label{sec:refinement}
@@
 \begin{defi}[Open automata refinement]
-For any two open automata \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), ``\(A_1\) is a refinement of \(A_2\)", noted \(A_1 \leq A_2\), is defined as:
+For two open automata \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), ``\(A_1\) is a refinement of \(A_2\) looking at \(H\)", noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), is defined as:
 \begin{multline*}
-	\exists R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2], \exists f: J_1 \setminus J_2 \to J_2 \setminus J_1, \\
-	\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}} \wedge R \text{ f simulation of } A_1 \text{ in } A_2
-\end{multline*}
-\end{defi}
-
-\begin{defi}[f simulation]
-\(R\) is a f simulation of \(A_1\) in \(A_2\) is defined as:
-\begin{multline*}
-	\forall s_1 \in S_1, s_2 \in S_2, \\
-	\mpar{\renewcommand\arraystretch{1.4}\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_1}}^{x \in X}, \\
-		\mpar{\forall x \in X, J'_1 \cap J_2 = J'_{2x} \cap J_1 \wedge f\mpar{J'_1 \setminus J_2} \subseteq J'_{2x}} \wedge \forall \sigma: \mpar{V_1 \uplus \fvars{t_1} \uplus V_2} \to \values, \\
-		\quad \sigma \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_1 \cap J_2} \beta_{1j} = \beta_{2xj} \\
+	\exists R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2], \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge \forall \mpar{s_1, s_2} \in S_1 \times S_2, \\
+	\mpar{\everymath{\displaystyle}\begin{array}{l}
+		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\[12pt]
+		\quad \mpar{\forall x \in X, J'_{2x} \cap J_1 \cap H = J'_1 \cap J_2 \cap H} \\[-10pt]
+		\quad \wedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2 \cap H} \beta_{1j} = \beta_{2xj} \\
 			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
@@
 	\end{array}} \\
-	\wedge \forall \sigma: \mpar{V_1 \uplus V_2} \to \values, R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
+	\wedge V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
 \end{multline*}
@@
 % Explain definition, really needed
-The objective of the first part of this definition is to be able to simulate \(A_1\) in \(A_2\) when holes of the same name receive the same closed automaton while other holes receive ``compatible" closed automata.
 % safety is no longer trivial, prove the safety
-The objective of the other part of this definition is to prevent the appearance of new deadlocks, which should mean with the first property that the compared automaton are deadlock equivalent.
-% Expected properties: no new deadlocks, every path can be simulated (safety), composition that do not introduce deadlock is refinement, congruence wrt composition 2-way, most refined are runs
+% Prove all expected properties except pre-simulation
 
-\section{New equivalence relation induced by pre-order}
-% FH-behaviourial equivalence if hole functions are not inverse, almost-FH-bisim if function is bijective and FH-bisim if in emptyset -> emptyset
+% What happens on untracked holes (untracked holes equivalent behaviour => free variables; some sort of daisy equivalence)
+% Yet having untracked holes is interesting because we can be a refinement of several OA, each on different holes.
+
+\section{Flat model}
+% Goal: some interfaces refine in one way while other refine in the other way and others are equivalent and some are untracked.
 
@@
 
+\section{Examples of hole-\(\triangle\) simulations}\label{apx:refrel}
+\subsection{Example of hole-equal simulation}
+\begin{exi}
+\begin{figure}
+\centering
+\input{parallel_comp.tex}
+\vrule
+\input{n_control_switch.tex}
+\caption{On the left: Parallel composition operator; On the right: n control switches automaton}
+\label{fig:hisim}
+\end{figure}
+To illustrate the definition and the different refinement operations, Figure \ref{fig:hisim} introduces two related open automata with same holes \(\mbrc{l, r}\).
+The automaton on the left is a parallel composition: any hole can perform actions at any time, the actions are passed unmodified and no synchronisation is performed.
+The automaton on the right is a sequential composition with \(n\) control switches: a hole performs a sequence of actions then the other does, there are \(n\) seqences of a single automaton doing actions without the other performing some.
+The initial valuation of the right automaton is in blue, actually we want to consider both the automaton with this initial valuation and the one without.
+
+Intuitively the right automaton is a refinement of the left automaton because the left automaton is what happens when there was no bound \(n\) in the right automaton.
+Also the right automaton with the initial valuation is a refinement of the right automaton with the initial valuation because a ``\(1\) control switches" is an instance of a ``\(n\) control switches".
+
+First let consider \(R\), a hole-identical simulation of \(n\) control switches by parallel composition:
+\[ R \defobject \mbrc{\mpar{l, ||} \mapsto \top, \mpar{r, ||} \mapsto \top} \]
+% TODO: continue
+\end{exi}
+
+% Hole-subset: Traffic lights
+% Hole-superset: scheduler
+
+% APB
+
+\section{Proof of transitivity}\label{apx:trans}
+Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) be open automata.
+Let \(R_{12}\) be a hole-\(\triangle\) simulation of \(A_1\) by \(A_2\) and \(R_{23}\) of \(A_2\) by \(A_3\).
+\[ R_{13} \defobject \mpar{s_1, s_3} \mapsto \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \]
+\(R_{13}\) is a hole-\(\triangle\) simulation of \(A_1\) by \(A_3\).
+\begin{proof}
+\defitem By transitivity of \(=\), \(J_1 = J_3\)
+\defitem We prove that initial configurations are related using \(\sigma_{02}\) as the values of the variables in \(V_2\), and \(s_2\) as the branch of the disjunction.
+\begin{gather*}
+	\sigma_{01} \uplus \sigma_{03} \vdash R_{13}\mpar{s_{01}, s_{03}} \\
+	\equiv \\
+	\sigma_{01} \uplus \sigma_{03} \vdash \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_{01}, s_2} \wedge R_{23}\mpar{s_2, s_{03}} \\
+	\Uparrow \\
+	\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03} \vdash R_{12}\mpar{s_{01}, s_{02}} \wedge R_{23}\mpar{s_{02}, s_{03}} \\
+	\Uparrow \\
+	\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar{\sigma_{02} \uplus \sigma_{03} \vdash R_{23}\mpar{s_{02}, s_{03}}}
+\end{gather*}
+\defitem Let \(\mpar{s_1, s_3} \in S_1 \times S_3\), we want to prove both
+\begin{multline}
+	\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{3x} \defobject \OTx{3}{x}{3x}{3x} \in \fOT{s_3}}^{x \in X}, \mpar{\forall x \in X, J'_{3x} = J'_1} \\
+	\wedge V_1 \uplus V_3 \uplus \fvars{t_1} \vdash R_{13}\mpar{s_1, s_3} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+		\alpha_1 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x}} \beta_{1j} = \beta_{3xj} \\[12pt]
+		\nwedge g_{3x} \wedge R_{13}\mpar{s'_1, s'_{3x}}\psubst{\psi_1 \uplus \psi_{3x}}
+	\end{array}} \goal{1}
+\end{multline}
+\[ V_1 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash R_{13}\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{2} \]
+\begin{description}
+	\item[\goal{2}:] Let \(\sigma_1: V_1 \to \values\) and \nmm{\sigma_3: V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \to \values} be such that
+	\[ \sigma_1 \uplus \sigma_3 \vdash R_{13}\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{2'} \]
+	We use dummy values for variables in \nmm{\biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1}} to get the left side of this implication as an hypothesis (independant from these values):
+	\[ \sigma_1 \uplus \sigma_3 \vdash R_{13}\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \hyp{5} \]
+	Hypothesis that we immediately break down into:
+	\begin{align}
+		\nu & : V_2 \to \values &
+		\sigma_1 \uplus \sigma_3 \uplus \nu & \vdash R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \hyp{5'} \\
+		t_3 & \in \fOT{s_3} &
+		\sigma_1 \uplus \sigma_3 & \vdash \fguard{t_3} \hyp{5"}
+	\end{align}
+	% TODO HERE
+\end{description}
+\end{proof}
+
 \end{document}

### 2021-05-31 2021-Refinement/report.tex
Transitivity proof WIP

@@
 % TODO: CITER LES CONFERENCES
+% change deadlock reduction into deadlock prevention?
 
@@
 \section{Composition of Open Automata}\label{sec:comp}
-% TODO: distinguish composition from "parallel composition (pure interleaving)"
 Open automata are partially specified automata, part of that partiality comes from the holes.
 The interpretation of a hole is an interface with another open automaton, in which we can plug an open automaton with an operation called composition.
+In this article, composition will only refer to filling holes, other compositions like ``parallel composition" (pure interleaving) are not tackled.
 The composition of open automata was already implicitely defined by the means of composition on pNets in previous work \cite{henrio:01299562} but never completely formalised on open automata.
@@
 \end{defi}
-
 The important properties we consider for the relation on automata are:
@@
 \end{defi}
-The last formula means that for every pair of related states under valuation of the automaton variables and every possible transitions (\(\vdash g_1\)) from the first automaton, there is a possible transition (\(\vdash g_2\)) such that the produced action matches (\(\alpha_1 = \alpha_2\)), the holes actions from same hole names (\(J'_1 \cap J'_2\)) match (\(\beta_{1j} = \beta_{2j}\)) and the target states are related after variable update.
-Apart from holes, this is a natural extension of the notion of simulation on LTS, which is the same definition without variables and holes and guards.
+The last formula means that for every pair of related states under valuation of the automaton variables and every possible transitions (\(\vdash g_1\)) from the first automaton, there is a possible transition (\(\vdash g_2\)) such that the produced action matches (\(\alpha_1 = \alpha_2\)), the same holes' action (\(J'_1 \cap J'_2\)) matches (\(\beta_{1j} = \beta_{2j}\)) and the target states are related after variable update.
+Apart from holes, this is a natural extension of the notion of simulation on LTS, which is the same definition without variables nor holes nor guards.
 In FH-bisimulation, holes with the same name will receive the same open automaton when composed, and the resulting open automaton will still be equivalent.
 Here we assume that one of the related open automata can be obtained by composing an open automaton in a hole, open automaton which can have holes itself.
-This implies that there is no relation between their holes, for instance composing \(A_i, 1 \leq i \leq n\) in \(A_0\) gives the holes \(J \defobject \mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{k_i}{1 \leq i \leq n} \) that is neither subset nor superset of \(J_0\).
+This implies that there is no relation between their holes, for instance composing \(A_i\) in \(j_i\) (\(1 \leq i \leq n\)) of \(A_0\) gives the set of holes \(J \defobject \mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n} \) that is neither subset nor superset of \(J_0\).
 Yet we still assume that in holes with the same name, the same open automaton will be composed.
@@
 
-Deadlocks are configurations reachable in a run and from which no further transition is possible.
+Deadlocks are reachable configurations and from which no further transition is possible.
 They can arise unpredictably when parallelism is involved (which is the case in our composition) and they break the intended behaviour of a system.
@@
 \end{defi}
-This requirement effectively prevents the presence of deadlock state in the first automaton if there is a related non-deadlock state in the second by contraposition.
+Actually, this requirement prevents the presence of deadlock state in the first automaton if there is a related non-deadlock state in the second by contraposition.
 On top of that the transition preventing the deadlock has to be an existing transition in the specification.
@@
 \begin{defi}[Reachability]
-For any open automata \(A \defobject \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is a predicate on states such that
-\defitem \(\sigma_0 \vdash \reach{A}\mpar{s_0}\)
-\defitem \nmm{\bigsymb{\forall} t \defobject \OTg \in T, \forall \nu: \fvars{t} \to \values, \nu \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}}
+For any open automata \(A \defobject \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is a predicate on states satisfying both
+\defitem Inital state is reachable: \(\sigma_0 \vdash \reach{A}\mpar{s_0}\)
+\defitem Reachability is preserved across transitions: \nmm{\bigsymb{\forall} t \defobject \OTg \in T, \forall \nu: \fvars{t} \to \values, \nu \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}}
 \end{defi}
-For the reader not used to simulations and bisimulations, this definition of a predicate can seem strange.
-The reachability predicate is used to characterise the states and valuations that are reachable in a run of an automaton.
+The reachability predicate is used to characterise the reachable configurations in a run of an automaton.
 In fact the role of the predicate is to characterise potentially reachable configurations without having to characterise configurations as the result of a valid path in an automaton.
@@
 This effectively makes reachability account for all paths and potentially over-approximate the reachable configurations.
-However the exact reachability may not be reprensentable in the formulas, hence the need of potentially over-approximating.
+The exact reachability may not be reprensentable in the formulas, hence the need of potentially over-approximating. % TODO: is representable the correct word
 
-Another way of understanding this predicate is that it is a fixpoint of the union of valuations (function \(f\) defined below) that contains the initial valuation:
-\begin{align*}
-	f\mpar{p} = \mbrc{\mbox{\nmm{s' \mapsto p\mpar{s'} \vee \bigsymb{\bigvee_\subbox{\OTg \,\in\, \fIT{s'}}} p\mpar{s}\psubst{\psi} \wedge g}}} && % TODO: fix that in some way
-	\sigma_0 \vdash \reach{A}\mpar{s_0} &&
-	f\mpar{\reach{A}} = \reach{A}
-\end{align*}
+% Another way of understanding this predicate is that it is a fixpoint of the union of valuations (function \(f\) defined below) that contains the initial valuation:
+% \begin{align*}
+	% f\mpar{p} = \mbrc{\mbox{\nmm{s' \mapsto p\mpar{s'} \vee \bigsymb{\bigvee_\subbox{\OTg \,\in\, \fIT{s'}}} p\mpar{s}\psubst{\psi} \wedge g}}} && % TODO: fix that in some way
+	% \sigma_0 \vdash \reach{A}\mpar{s_0} &&
+	% f\mpar{\reach{A}} = \reach{A}
+% \end{align*}
+\begin{defi}[Non-locking composition, intuitive definition]
+Let \(A_c \defobject \OAg[c]\), \(A_p \defobject \OAg[p]\) and \(j \in J_p\).
+The composition \(A \defobject A_p\subst{A_c}{j}\) is non-locking if \(A\) has a reachability predicate satisfying:
+From reachable configurations, if there was a possible transition in \(A_p\) then there is a possible transition in \(A_p\subst{A_c}{j}\).
 
-\begin{defi}[Non-locking composition, intuitive definition]
-Let \(A_p\subst{A_c}{j} = \OAg\) with \(A_c \defobject \OAg[c]\), \(A_p \defobject \OAg[p]\) and \(j \in J_p\).
-The composition is non-locking if there is a reachability predicate such that from reachable configurations, if there was a possible transition in \(A_p\) then there is a possible transition in \(A_p\subst{A_c}{j}\):
+In formula, for \(A = \OAg\), it gives
 \begin{multline*}
 	\forall s \defobject \mpar{s_p, s_c} \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A_p\subst{A_c}{j}}\mpar{s}} \implies \\
-	\mpar{\exists t_p \in \fOT{s_p}, \exists \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \vdash \fguard{t_p}} \implies \\
+	\mpar{\exists t_p \in \fOT{s_p}, \exists \nu_p: \fvars{t_p} \to \values, \sigma \uplus \nu_p \vdash \fguard{t_p}} \implies \\
 	\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t}
@@
 \end{defi}
-An illustration of the introduction of a deadlock by composition and the definition of non-locking composition is given in Appendix \ref{apx:lockcomp}.
-
-We can expand the aliases \(S, V\) into \(S_p \times S_c, V_p \uplus V_c\) and the last transition \(t\) into a pair \(\mpar{t_p, t}\) where the first transition is the one from \(A_p\) which generated \(t\).
-Doing that makes the definition become mildly similar with the deadlock reduction one.
+We can expand the aliases \(S, V\) into \(S_p \times S_c, V_p \uplus V_c\) and transform the last transition \(t\) into a pair \(\mpar{t_p, t}\) where the first transition is the one from \(A_p\) which generated \(t\).
+Doing that makes the definition become mildly similar with the deadlock reduction one. % OR slightly
 It is not a coincidence because their goal is to caracterise the same kind of compatibility between automata.
@@
 \begin{defi}[Deadlock reduction, working definition]
-A relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if it is a pre-simulation and:
+A relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if it is a pre-simulation and it satisfies the following:
 \begin{multline*}
@@
 The expected advantage of this formulation is that a SMT should behave better without the quantifiers.
-Indeed the big disjunctions are not quantifiers because in practise the out-transitions are finitary, and so is the expansion of the disjunction.
+Indeed the big disjunctions are not quantifiers because in practise the out-transitions are finitary, and so is the expansion of the disjunction. % WHAT IS THE ISSUE HERE?
 \begin{lem}
@@
 \end{lem}
-
 \begin{defi}[Non-locking composition, working definition]
@@
 \end{lem}
+An illustration of the introduction of a deadlock by composition and the definition of non-locking composition is given in Appendix \ref{apx:lockcomp}.
 Proof of both lemma are given in Appendix \ref{apx:lemeqd}.
 
-This new definition of composition can replace the standard composition in the case where only one hole is filled, and also in the parallel case.
-In the parallel case, we may think that if the condition is checked in the parallel case (at the final composition), then the composition is non-locking for every composition order.
+This new definition of composition can replace the standard composition in the case where only one hole is filled, and also be extended to a parallel composition.
+For the parallel composition, we may think that if the composition is non-locking, then every composition is non-locking for all composition order.
 It is not true.
-Actually even if the last composition of any order of composition is non-locking there is no guarantee that this order is non-locking at every step.
-However the oppsite way is true even if uninformative:
+Actually even if the last composition of any order of composition is non-locking there is no guarantee that this order is non-locking at each step.
+However the oppsite way is true even if uninformative: % WHAT IS THE ISSUE?
 If there is an order of composition where every composition is non-locking then the last composition is non-locking, last composition resulting in the same automaton as the parallel composition.
@@
 
-\section{Refinement relations in restricted cases}\label{sec:prelref} % TODO: Fold definitions and proofs
+\section{Refinement relations in restricted cases}\label{sec:prelref}
 The main goal of this section is to explain the different aspects of refinement in restricted cases so that they are not all introduced at once in the real refinement relation.
@@
 		\quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
-		\quad \wedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
 			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
 			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}} \\[12pt]
+		\end{array}}
 	\end{array}} \\
@@
 		\quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
-		\quad \wedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
 			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
@@
 \nmm{R_{13} \defobject \mpar{s_1, s_3} \mapsto \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}} is a witness of the transitivity, proof is given in appendix \ref{apx:trans}.
-\begin{thm}[Context refinement]
-% a <= b & a[c] <= a -> a[c] <= b[c]
-\end{thm}
+\begin{thm}[Context refinement] Hole-equal simulation is context refining \end{thm}
 \begin{proof}
+% TODO: assume a <= b & a[c] -> b[c] + proof
 \end{proof}
 % Rédiger un paragraphe sur le fait que composer dans l'implem sans deadlock implique qu'il n'y a pas de deadlock quand on compose avec la spec, on voudrais avoirs l'autre sens mais ce n'est pas possible
-\begin{prop}[Composition correctness']
-% TODO: Proof that filling holes with a fully specified automaton is a refinement
+\begin{prop}[Composition correctness'] Hole-subset simulation is correct w.r.t.\@ composition. \end{prop}
+\begin{proof}
+% TODO
+\end{proof}
+\begin{prop}[Composition correctness"]
+Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3\) be open automata.
+If \(R\) is a hole-superset simulation of \(A_1\) by \(A_2\) then let \(j \in J_1 \setminus J_2\), there is a hole-superset simulation of \(A_1\subst{A_3}\) by \(A_2\).
 \end{prop}
 \begin{proof}
-\end{proof}
-\begin{prop}[Composition correctness"]
-% TODO: Proof that filling added holes with a fully specified automaton is a refinement
-\end{prop}
-\begin{proof}
+% TODO
 \end{proof}
@@
 	However we cannot yet prove it because we don't know whether \(t_2\) and \(t_1\) do match.
-	In order to get a \(t_2\) matching \(t_1\) we use will use \hyp{0}.
-	\hyp{0} with current value of \(\mpar{s_1, s_2}\), \(t_1\) and \(\sigma \uplus \mu\) as a valuation of \(V_1 \uplus V_2 \uplus \fvars{t_1}\) gives:
+	In order to get a \(t_2\) matching \(t_1\) we use will use \eqref{eq:drID}.
+	\eqref{eq:drID} with current value of \(\mpar{s_1, s_2}\), \(t_1\) and \(\sigma \uplus \mu\) as a valuation of \(V_1 \uplus V_2 \uplus \fvars{t_1}\) gives:
 	\begin{multline}
@@
 \begin{proof}
-\defitem By transitivity of \(=\), \(J_1 = J_3\)
+\defitem By transitivity of \(\triangle\), \(J_1 \triangle J_3\)
 \defitem We prove that initial configurations are related using \(\sigma_{02}\) as the values of the variables in \(V_2\), and \(s_2\) as the branch of the disjunction.
@@
 \begin{multline}
-	\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{3x} \defobject \OTx{3}{x}{3x}{3x} \in \fOT{s_3}}^{x \in X}, \mpar{\forall x \in X, J'_{3x} = J'_1} \\
+	\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{3x} \defobject \OTx{3}{x}{3x}{3x} \in \fOT{s_3}}^{x \in X}, \\
+	\mpar{\forall x \in X, J'_{3x} \cap J_1 = J'_1 \cap J_3} \\
 	\wedge V_1 \uplus V_3 \uplus \fvars{t_1} \vdash R_{13}\mpar{s_1, s_3} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-		\alpha_1 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x}} \beta_{1j} = \beta_{3xj} \\[12pt]
+		\alpha_1 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x} \cap J_1} \beta_{1j} = \beta_{3xj} \\[12pt]
 		\nwedge g_{3x} \wedge R_{13}\mpar{s'_1, s'_{3x}}\psubst{\psi_1 \uplus \psi_{3x}}
-	\end{array}} \goal{1}
+	\end{array}} \goal{0}
 \end{multline}
-\[ V_1 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash R_{13}\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{2} \]
+\[ V_1 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash R_{13}\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{1} \]
 \begin{description}
-	\item[\goal{2}:] Let \(\sigma_1: V_1 \to \values\) and \nmm{\sigma_3: V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \to \values} be such that
-	\[ \sigma_1 \uplus \sigma_3 \vdash R_{13}\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{2'} \]
+	\item[\goal{0}:] Let \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}}.
+	We have the hypotheses on \(R_{12}\) and \(R_{23}\), then the current goal:
+	\[
+		\everymath{\displaystyle}\begin{array}{l}
+		\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
+		\quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
+		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R_{12}\mpar{s_1, s_2} \wedge g_1 \Rightarrow \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\!\!\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
+			\nwedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}\!\!}
+		\end{array} \hyp{0}
+	\]\[
+		\everymath{\displaystyle}\begin{array}{l}
+		\bigsymb{\forall} t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \bigsymb{\exists} \mpar{t_{3x} \defobject \OTx{3}{x}{3x}{3x} \in \fOT{s_3}}^{x \in X}, \\
+		\quad \mpar{\forall x \in X, J'_{3x} \cap J_2 = J'_2 \cap J_3} \\[-10pt]
+		\nwedge V_2 \uplus V_3 \uplus \fvars{t_2} \vdash R_{23}\mpar{s_2, s_3} \wedge g_2 \Rightarrow \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\!\!\begin{array}{l}
+			\alpha_2 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x} \cap J_2} \beta_{2j} = \beta_{3xj} \\[12pt]
+			\nwedge g_{3x} \wedge R_{23}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
+		\end{array}\!\!}
+		\end{array} \hyp{1}
+	\]\[
+		\everymath{\displaystyle}\begin{array}{l}
+		\bigsymb{\exists} \mpar{t_{3x} \defobject \OTx{3}{x}{3x}{3x} \in \fOT{s_3}}^{x \in X}, \mpar{\forall x \in X, J'_{3x} \cap J_1 = J'_1 \cap J_3} \\[-4pt]
+		\nwedge V_1 \uplus V_3 \uplus \fvars{t_1} \vdash R_{13}\mpar{s_1, s_3} \wedge g_1 \Rightarrow \!\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\!\!\begin{array}{l}
+			\alpha_1 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x} \cap J_1} \beta_{1j} = \beta_{3xj} \\[12pt]
+			\nwedge g_{3x} \wedge R_{13}\mpar{s'_1, s'_{3x}}\psubst{\psi_1 \uplus \psi_{3x}}
+		\end{array}\!\!}
+		\end{array} \goal{0'}
+	\]
+	We use hypothesis \hyp{0} with \(t_1\) to get
+	\begin{gather*}
+		\mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X} \\
+		\mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \hyp{0'} \\
+		V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R_{12}\mpar{s_1, s_2} \wedge g_1 \Rightarrow \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
+			\nwedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}} \hyp{0"}
+	\end{gather*}
+	Then use \hyp{1} with every \(t_{2x}\) to get
+	\begin{gather*}
+		\mpar{t_{3xy} \defobject \OTx{3}{xy}{3xy}{3xy} \in \fOT{s_3}}^{y \in Y_x} \\
+		\mpar{\forall y \in Y_x, J'_{3xy} \cap J_2 = J'_{2x} \cap J_3} \hyp{1x} \\
+		V_2 \uplus V_3 \uplus \fvars{t_{2x}} \vdash R_{23}\mpar{s_2, s_3} \wedge g_{2x} \Rightarrow \operatorname*{\bigsymb{\bigvee}}_{y \in Y_x} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{2x} = \alpha_{3xy} \wedge \bigwedge_\subbox{j \in J'_{3xy} \cap J_2} \beta_{2xj} = \beta_{3xyj} \\[12pt]
+			\nwedge g_{3xy} \wedge R_{23}\mpar{s'_{2x}, s'_{3xy}}\psubst{\psi_{2x} \uplus \psi_{3xy}}
+		\end{array}} \hyp{1x'}
+	\end{gather*}
+	We pose \(Z \defobject \mset{\mpar{x, y}}{x \in X, y \in Y_x}\).
+	We will prove \goal{0'} for the family \(t_{3xy}^{\mpar{x, y} \in Z}\).
+	The new goals are:
+	\begin{gather}
+		\forall \mpar{x, y} \in Z, J'_{3xy} \cap J_1 = J'_1 \cap J_3 \goal{2} \\
+		V_1 \uplus V_3 \uplus \fvars{t_1} \vdash R_{13}\mpar{s_1, s_3} \wedge g_1 \Rightarrow \hspace{-3mm}\operatorname*{\bigsymb{\bigvee}}_{\mpar{x, y} \in Z}\!\!\mpar{\!\!\everymath{\displaystyle}\begin{array}{l}
+			\alpha_1 = \alpha_{3xy} \wedge \bigwedge_\subbox{j \in J'_{3xy} \cap J_1} \beta_{1j} = \beta_{3xyj} \\[12pt]
+			\nwedge g_{3xy} \wedge R_{13}\mpar{s'_1, s'_{3xy}}\psubst{\psi_1 \uplus \psi_{3xy}}
+		\end{array}\!\!} \goal{3}
+	\end{gather}
+	For \goal{2} the proof depends on \(\triangle\).
+	\begin{itemize}
+	\item Let \(\triangle\) be \(\subseteq\).
+		\begin{align*}
+		J'_{3xy} \cap J_1 & \subseteq J'_{3xy} \cap J_2 & \text{by } & J_1 \subseteq J_2 \\
+			& \subseteq J'_{2x} \cap J_3 & \text{by } & \text{\hyp{1x}} \\
+			& \subseteq J'_{2x} \cap J_3 \cap J_1 & \text{by } & J'_{3xy} \cap J_1 \subseteq J_1 \\
+			& \subseteq J'_{2x} \cap J_1 && \\
+			& \subseteq J'_1 \cap J_2 & \text{by } & \text{\hyp{0'}} \\
+			& \subseteq J'_1 \cap J_3 & \text{by } & J_2 \subseteq J_3
+		\end{align*}
+		\begin{align*}
+		J'_1 \cap J_3 & = J'_1 = J'_1 \cap J_2 & \text{by } & J'_1 \subseteq J_1 \subseteq J_2 \subseteq J_3 \\
+			& = J'_{2x} \cap J_1 & \text{by } & \text{\hyp{0'}} \\
+			& \subseteq J'_{2x} \cap J_3 & \text{by } & J_1 \subseteq J_3 \\
+			& \subseteq J'_{3xy} \cap J_2 & \text{by } & \text{\hyp{1x}} \\
+			& \subseteq J'_{3xy} \cap J_2 \cap J_1 & \text{by } & J'_1 \subseteq J_1 \\
+			& \subseteq J'_{3xy} \cap J_1 &&
+		\end{align*}
+		Hence \goal{2} holds.
+	\item Let \(\triangle\) be \(\supseteq\).
+		\begin{align*}
+		J'_1 \cap J_3 & \subseteq J'_1 \cap J_2 & \text{by } & J_3 \supseteq J_2 \\
+			& \subseteq J'_{2x} \cap J_1 & \text{by } & \text{\hyp{0'}} \\
+			& \subseteq J'_{2x} \cap J_1 \cap J_3 & \text{by } & J'_1 \cap J_3 \subseteq J_3 \\
+			& \subseteq J'_{2x} \cap J_3 && \\
+			& \subseteq J'_{3xy} \cap J_2 & \text{by } & \text{\hyp{1x}} \\
+			& \subseteq J'_{3xy} \cap J_1 & \text{by } & J_1 \supseteq J_2
+		\end{align*}
+		\begin{align*}
+		J'_{3xy} \cap J_1 & = J'_{3xy} = J'_{3xy} \cap J_2 & \text{by } & J_1 \supseteq J_2 \supseteq J_3 \supseteq J'_{3xy} \\
+			& = J'_{2x} \cap J_3 & \text{by } & \text{\hyp{1x}} \\
+			& \subseteq J'_{2x} \cap J_1 & \text{by } & J_1 \supseteq J_3 \\
+			& \subseteq J'_1 \cap J_2 & \text{by } & \text{\hyp{0'}} \\
+			& \subseteq J'_1 \cap J_2 \cap J_3 & \text{by } & J'_{3xy} \subseteq J_3 \\
+			& \subseteq J'_1 \cap J_3 &&
+		\end{align*}
+		Hence \goal{2} holds.
+	\item Let \(\triangle\) be \(=\).
+		We combine the proofs for two above cases and get both inclusions so \goal{2} holds.
+	\end{itemize}
+	Now the proof for \goal{3}.
+	% TODO HERE: goal 3
+	\item[\goal{1}:] Let \(\sigma_1: V_1 \to \values\) and \nmm{\sigma_3: V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \to \values}.
+	We have the hypotheses on \(R_{12}\) and \(R_{23}\), then the current goal:
+	\begin{gather}
+		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6} \\
+		V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash R_{23}\mpar{s_2, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{7} \\
+		\sigma_1 \uplus \sigma_3 \vdash R_{13}\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{1'}
+	\end{gather}
 	We use dummy values for variables in \nmm{\biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1}} to get the left side of this implication as an hypothesis (independant from these values):
@@
 	\begin{align}
-		\nu & : V_2 \to \values &
-		\sigma_1 \uplus \sigma_3 \uplus \nu & \vdash R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \hyp{5'} \\
-		t_3 & \in \fOT{s_3} &
-		\sigma_1 \uplus \sigma_3 & \vdash \fguard{t_3} \hyp{5"}
+		\sigma_2 & : V_2 \to \values &
+		\sigma_1 \uplus \sigma_2 \uplus \sigma_3 & \vdash R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \hyp{5'} \\
+		&& \sigma_1 \uplus \sigma_3 & \vdash \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \hyp{5"}
 	\end{align}
-	% TODO HERE
+	We can use immediately \hyp{7} with valuation \(\sigma_2 \uplus \sigma_3\) to get \(\nu_2: \biguplus_{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values\).
+	The left side of the implication is proved with the right side of \hyp{5'} and \hyp{5"}, so we get
+	\[ \sigma_2 \uplus \sigma_3 \uplus \nu_2 \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{7'} \]
+	We can now use \hyp{6} with valuation \(\sigma_1 \uplus \sigma_2 \uplus \nu_2\) to get \(\nu_1: \biguplus_{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values\).
+	The left side of the implication is proved with the left side of \hyp{5'} and \hyp{7'}, so we get
+	\[ \sigma_1 \uplus \sigma_2 \uplus \nu_1 \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6'} \]
+	Finally we can prove \goal{1'} with valuation \(\nu_1\) fot the implicit \(\exists\) by admitting the left side of the implication and using \hyp{6'} for the right side.
 \end{description}

### 2021-05-31 2021-Refinement/report.tex
Added comments in source to not pretend the proof is complete

@@
 \begin{prop}[Composition correctness"]
-Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3\) be open automata.
-If \(R\) is a hole-superset simulation of \(A_1\) by \(A_2\) then let \(j \in J_1 \setminus J_2\), there is a hole-superset simulation of \(A_1\subst{A_3}\) by \(A_2\).
+Let \(A_1 \defobject \OAg[1]\) be hole-superset simulated by \(A_2 \defobject \OAg[2]\).
+Let \(j \in J_1 \setminus J_2\) and \(A_3\) an open automaton.
+There is a hole-superset simulation of \(A_1\subst{A_3}{j}\) by \(A_2\).
 \end{prop}
@@
 \defitem By transitivity of \(\triangle\), \(J_1 \triangle J_3\)
-\defitem We prove that initial configurations are related using \(\sigma_{02}\) as the values of the variables in \(V_2\), and \(s_2\) as the branch of the disjunction.
+\defitem We prove that initial configurations are related using \(\sigma_{02}\) as the values of the variables in \(V_2\), and \(s_{02}\) as the branch of the disjunction.
 \begin{gather*}
@@
 \begin{description}
-	\item[\goal{0}:] Let \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}}.
+	\item[\goal{0}:] Let \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}}. % TODO: quantify on s_2
 	We have the hypotheses on \(R_{12}\) and \(R_{23}\), then the current goal:
@@
 	Now the proof for \goal{3}.
-	% TODO HERE: goal 3
+	Let \(\sigma_1: V_1 \uplus \fvars{t_1} \to \values\) and \(\sigma_3: V_3 \to \values\).
+	We use dummy values for variables in \nmm{\biguplus_\subbox{\mpar{x, y} \in Z} \fvars{t_{3xy}}} to get the left side of this implication as an hypothesis (independant from these values):
+	\[ \sigma_1 \uplus \sigma_3 \vdash R_{13}\mpar{s_1, s_3} \wedge g_1 \hyp{2} \]
+	Hypothesis that we immediately break down into:
+	\begin{align}
+		\sigma_2 & : V_2 \to \values &
+		\sigma_1 \uplus \sigma_2 \uplus \sigma_3 & \vdash R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \hyp{2'} \\
+		&& \sigma_1 & \vdash g_1 \hyp{2"}
+	\end{align}
+	We can use immediately \hyp{0"} with valuation \(\sigma_1 \uplus \sigma_2\) to get \nmm{\nu_2: \biguplus_{x \in X} \fvars{t_{2x}} \to \values}.
+	The left side of the implication is proved with the right side of \hyp{2'} and \hyp{2"}, so we get \(x \in X\) and the hypotheses
+	\begin{align}
+		\sigma_1 \uplus \sigma_2 \uplus \nu_2 & \vdash \alpha_1 = \alpha_{2x} \hyp{3a} \\
+		\sigma_1 \uplus \sigma_2 \uplus \nu_2 & \vdash \bigwedge_\subbox{j \in J'_1 \cap J'_{2x}} \beta_{1j} = \beta_{2xj} \hyp{3b} \\
+		\sigma_2 \uplus \nu_2 & \vdash g_{2x} \hyp{3c} \\
+		\sigma_1 \uplus \sigma_2 \uplus \nu_2 & \vdash R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \hyp{3d}
+	\end{align}
+	We can now use \hyp{1x'} with valuation \(\sigma_2 \uplus \nu_2 \uplus \sigma_3\) to get \nmm{\nu_3: \biguplus_{y \in Y_x} \fvars{t_{3xy}} \to \values}.
+	The left side of the implication is proved with the left side of \hyp{2'} and \hyp{2"}, so we get \(y \in Y_x\) and the hypotheses
+	\begin{align}
+		\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3 & \vdash \alpha_{2x} = \alpha_{3xy} \hyp{4a} \\
+		\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3 & \vdash \bigwedge_\subbox{j \in J'_{2x} \cap J'_{3xy}} \beta_{2xj} = \beta_{3xyj} \hyp{4b} \\
+		\sigma_3 \uplus \nu_3 & \vdash g_{3xy} \hyp{4c} \\
+		\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3 & \vdash R\mpar{s'_{2x}, s'_{3xy}}\psubst{\psi_{2x} \uplus \psi_{3xy}} \hyp{4d}
+	\end{align}
+	Finally to prove \goal{3} with valuation \(\nu_3\) for the implicit \(\exists\), we admit the left side of the implication choose to prove the branch \(\mpar{x, y}\):
+	\begin{align}
+		\sigma_1 \uplus \sigma_3 \uplus \nu_3 & \vdash \alpha_1 = \alpha_{3xy} \goal{3a} \\
+		\sigma_1 \uplus \sigma_3 \uplus \nu_3 & \vdash \bigwedge_\subbox{j \in J'_{3xy} \cap J_1} \beta_{1j} = \beta_{3xyj} \goal{3b} \\
+		\sigma_3 \uplus \nu_3 & \vdash g_{3xy} \goal{3c} \\
+		\sigma_1 \uplus \sigma_3 \uplus \nu_3 &\vdash R_{13}\mpar{s'_1, s'_{3xy}}\psubst{\psi_1 \uplus \psi_{3xy}} \goal{3d}
+	\end{align}
+	\goal{3a} is proved by transitivity using \hyp{3a} and \hyp{4a}.
+	\goal{3b} depends on \(\triangle\).
+	If \(\triangle\) is \(\subseteq\) % TODO
+	If \(\triangle\) is \(\supseteq\) % TODO
+	\goal{3c} is exactly \hyp{4c}.
+	\goal{3d} % TODO: branch s_2
 	\item[\goal{1}:] Let \(\sigma_1: V_1 \to \values\) and \nmm{\sigma_3: V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \to \values}.
-	We have the hypotheses on \(R_{12}\) and \(R_{23}\), then the current goal:
+	We have the hypotheses on \(R_{12}\) and \(R_{23}\), then the current goal: % TODO HERE: get s_2 by decomposing R_{13}
 	\begin{gather}
-		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6} \\
-		V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash R_{23}\mpar{s_2, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{7} \\
+		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{5} \\
+		V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash R_{23}\mpar{s_2, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{6} \\
 		\sigma_1 \uplus \sigma_3 \vdash R_{13}\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{1'}
@@
 	We use dummy values for variables in \nmm{\biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1}} to get the left side of this implication as an hypothesis (independant from these values):
-	\[ \sigma_1 \uplus \sigma_3 \vdash R_{13}\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \hyp{5} \]
+	\[ \sigma_1 \uplus \sigma_3 \vdash R_{13}\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \hyp{7} \]
 	Hypothesis that we immediately break down into:
@@
 		\sigma_2 & : V_2 \to \values &
-		\sigma_1 \uplus \sigma_2 \uplus \sigma_3 & \vdash R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \hyp{5'} \\
-		&& \sigma_1 \uplus \sigma_3 & \vdash \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \hyp{5"}
+		\sigma_1 \uplus \sigma_2 \uplus \sigma_3 & \vdash R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \hyp{7'} \\
+		&& \sigma_1 \uplus \sigma_3 & \vdash \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \hyp{7"}
 	\end{align}
-	We can use immediately \hyp{7} with valuation \(\sigma_2 \uplus \sigma_3\) to get \(\nu_2: \biguplus_{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values\).
-	The left side of the implication is proved with the right side of \hyp{5'} and \hyp{5"}, so we get
-	\[ \sigma_2 \uplus \sigma_3 \uplus \nu_2 \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{7'} \]
-	We can now use \hyp{6} with valuation \(\sigma_1 \uplus \sigma_2 \uplus \nu_2\) to get \(\nu_1: \biguplus_{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values\).
-	The left side of the implication is proved with the left side of \hyp{5'} and \hyp{7'}, so we get
-	\[ \sigma_1 \uplus \sigma_2 \uplus \nu_1 \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6'} \]
-	Finally we can prove \goal{1'} with valuation \(\nu_1\) fot the implicit \(\exists\) by admitting the left side of the implication and using \hyp{6'} for the right side.
+	We can use immediately \hyp{6} with valuation \(\sigma_2 \uplus \sigma_3\) to get \nmm{\nu_2: \biguplus_{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values}.
+	The left side of the implication is proved with the right side of \hyp{7'} and \hyp{7"}, so we get
+	\[ \sigma_3 \uplus \nu_2 \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{6'} \]
+	We can now use \hyp{5} with valuation \(\sigma_1 \uplus \sigma_2 \uplus \nu_2\) to get \nmm{\nu_1: \biguplus_{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
+	The left side of the implication is proved with the left side of \hyp{7'} and \hyp{6'}, so we get
+	\[ \sigma_1 \uplus \nu_1 \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{5'} \]
+	Finally we can prove \goal{1'} with valuation \(\nu_1\) for the implicit \(\exists\) by admitting the left side of the implication and using \hyp{5'} for the right side.
 \end{description}

### 2021-06-01 2021-Refinement/report.tex
Changes suggested by Rabea

@@
 \begin{exi}[Enable, variable-oriented]
-The automaton drawn on the right side of Figure \ref{fig:enable} is \(\OA{\mbrc{»}}{»}{\mbrc{v}}{v \mapsto l}{\mbrc{l, r}}{T}\) where transitions in \(T\) are:
+The automaton drawn on the right side of Figure \ref{fig:enable} is \(\OA{\mbrc{»}}{»}{\mbrc{v}}{\mbrc{v \mapsto l}}{\mbrc{l, r}}{T}\) where transitions in \(T\) are:
 \begin{align*}
@@
 Intuitively it holds because the cartesian product of states, the union of sets, the union of maps and the conjunction on formulas (in the guards) are commutative and associative.
-This allows us to define the parallel composition \(A\psubst{A_j^{j \in J'}}\) as the result of any order of (sequential) composition where each \(A_j\) is composed in the hole \(j\).
-% OR pcomp [[j |-> A_j]]
+This allows us to define the simultaneous composition \(A\psubst{A_j^{j \in J'}}\) as the result of any order of (sequential) composition where each \(A_j\) is composed in the hole \(j\).
+% psubst to pcomp macro [[]]
 
@@
 
-The important properties we consider for the relation on states are being a simulation and the reduction of deadlocks as defined in the following definitions.
+The important properties we consider for the relation on states are being a simulation and the prevention of deadlocks as defined in the following definitions.
 \begin{defi}[Pre-simulation]
@@
 \end{defi}
-The last formula means that for every pair of related states under valuation of the automaton variables and every possible transitions (\(\vdash g_1\)) from the first automaton, there is a possible transition (\(\vdash g_2\)) such that the produced action matches (\(\alpha_1 = \alpha_2\)), the same holes' action (\(J'_1 \cap J'_2\)) matches (\(\beta_{1j} = \beta_{2j}\)) and the target states are related after variable update.
+The last formula means that for every pair of related configurations of the automaton and every possible transitions (\(\vdash g_1\)) from the first automaton, there is a possible transition (\(\vdash g_2\)) such that the produced action matches (\(\alpha_1 = \alpha_2\)), the same holes' action (\(J'_1 \cap J'_2\)) matches (\(\beta_{1j} = \beta_{2j}\)) and the target states are related after variable update.
+% OR variableS
 Apart from holes, this is a natural extension of the notion of simulation on LTS, which is the same definition without variables nor holes nor guards.
@@
 
-Deadlocks are reachable configurations and from which no further transition is possible.
+Deadlocks are reachable configurations from which no further transition is possible.
 They can arise unpredictably when parallelism is involved (which is the case in our composition) and they break the intended behaviour of a system.
 By preventing them we could hope that the refinement preserves some liveness properties.
-\begin{defi}[Deadlock reduction, intuitive definition]
+\begin{defi}[Deadlock prevention, intuitive definition]
 A relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if:
@@
 
-``Deadlock reduction" conflicts with all the properties where composition is involved (for instance ``composition correctness") by disallowing some unwanted cases where an automaton in a hole cannot produce any action that any out-transition expects.
+``Deadlock prevention" conflicts with all the properties where composition is involved (for instance ``composition correctness") by disallowing some unwanted cases where an automaton in a hole cannot produce any action that any out-transition expects.
 In particular filling a hole with the deadlock automaton (only one state without out-transitions) is not considered a refinement for a deadlock reducing relation.
@@
 To do that we impose that the initial configuration is reachable and that reachability is preserved by taking valid transitions.
-This effectively makes reachability account for all paths and potentially over-approximate the reachable configurations.
-The exact reachability may not be reprensentable in the formulas, hence the need of potentially over-approximating. % TODO: is representable the correct word
+This effectively makes reachability take into account all paths, and potentially over-approximate the reachable configurations.
+The exact reachability may not be representable in the formulas, hence the need of potentially over-approximating.
 
@@
 
-In formula, for \(A = \OAg\), it gives
+Formally for \(A = \OAg\), it gives
 \begin{multline*}
@@
 We can expand the aliases \(S, V\) into \(S_p \times S_c, V_p \uplus V_c\) and transform the last transition \(t\) into a pair \(\mpar{t_p, t}\) where the first transition is the one from \(A_p\) which generated \(t\).
-Doing that makes the definition become mildly similar with the deadlock reduction one. % OR slightly
+Doing that makes the definition become mildly similar with the deadlock prevention one. % OR slightly
 It is not a coincidence because their goal is to caracterise the same kind of compatibility between automata.
 Actually it is possible to simplify both definition and make them even more similar.
-\begin{defi}[Deadlock reduction, working definition]
+\begin{defi}[Deadlock prevention, working definition]
 A relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if it is a pre-simulation and it satisfies the following:
@@
 The expected advantage of this formulation is that a SMT should behave better without the quantifiers.
-Indeed the big disjunctions are not quantifiers because in practise the out-transitions are finitary, and so is the expansion of the disjunction. % WHAT IS THE ISSUE HERE?
+Indeed the big disjunctions are not quantifiers because in practise the out-transitions are finitary, and so is the expansion of the disjunction. % Check if that construction is correct
 \begin{lem}
-The intuitive and working definition of deadlock reduction are equivalent.
+The intuitive and working definition of deadlock prevention are equivalent.
 \end{lem}
@@
 \end{lem}
-An illustration of the introduction of a deadlock by composition and the definition of non-locking composition is given in Appendix \ref{apx:lockcomp}.
+An illustration of both the introduction of a deadlock by composition and the definition of non-locking composition is given in Appendix \ref{apx:lockcomp}.
 Proof of both lemma are given in Appendix \ref{apx:lemeqd}.
 
-This new definition of composition can replace the standard composition in the case where only one hole is filled, and also be extended to a parallel composition.
-For the parallel composition, we may think that if the composition is non-locking, then every composition is non-locking for all composition order.
-It is not true.
-Actually even if the last composition of any order of composition is non-locking there is no guarantee that this order is non-locking at each step.
-However the oppsite way is true even if uninformative: % WHAT IS THE ISSUE?
-If there is an order of composition where every composition is non-locking then the last composition is non-locking, last composition resulting in the same automaton as the parallel composition.
-So the condition is better checked after the parallel composition or the last individual composition.
+This new definition of composition can replace the standard composition in the case where only one hole is filled, and also be extended to a simultaneous composition.
+For the simultaneous composition, we may think that if the last composition of a specific composition order is non-locking, then every composition is non-locking for all composition order. % orderS
+Unfortunately it is not true.
+Actually even if the last composition of any order of composition is non-locking there is no guarantee that this order is non-locking at each intermediate step.
+However the opposite way is true even if uninformative:
+If there is an order of composition where every composition is non-locking then the last composition is non-locking, last composition resulting in the same automaton as the simultaneous composition.
+So the condition is better checked after the simultaneous composition or the last individual composition.
 \begin{exi}
@@
 The automaton on Figure \ref{fig:pnls} is a sample protocol for file synchronisation.
-The two holes are \(net\) a network manager used to perform operations on the network, and \(hash\) a file integrity check used to generate a fingerprint.
+The two holes are \(net\) a process to manage network communications, and \(hash\) a process to check files integrity.
 The state \(i\) is the initial state.
 In that state we want to synchronise the files before working, or work on the local version as a fallback.
-If the preferred version is the remote one, we go in state \(d1\) asking the netwotk manager to fetch the lastest version, then ask the integrity checker to validate the fingerprint.
-If the preferred version is the local one, we go in state \(d2\) asking for the integrity checker to generate a fingerprint for the local files, then ask the network manager to push them.
+If the preferred version is the remote one, we go in state \(d1\) asking the netwotk manager to fetch the lastest version, then ask the integrity checker to validate the files.
+If the preferred version is the local one, we go in state \(d2\) asking for the integrity checker to validate the local files, then ask the network manager to push them.
 In fallback we use the local version.
 
-We can debranch the network manager and the file integrity check by composing a deadlock automaton in their holes, but always both at the same time.
-The reason for that is the parallel composition is non-locking, but any individual composition is locking because the state \(d1\) or \(d2\) (depending on the order) becomes a deadlock.
+We can plug an inactive process for the network manager and the file integrity checker by composing a deadlock automaton in their holes, but always both at the same time.
+The reason for that is the simultaneous composition is non-locking, but any individual composition is locking because the state \(d1\) or \(d2\) (depending on the order) becomes a deadlock.
 \end{exi}
@@
 In particular if we have a family of open automata \(A_i \defobject \OAg[i]\), \(0 \leq i \leq n\), let \(A \defobject \OAg\) be such that \(A = A_0\psubst{j_i \mapsto A_i \middle| 1 \leq i \leq n}\).
-Recall that there is no relation between the holes of \(A\) and \(A_0\) because \(J = \mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{i \in \mdbrk{1; n}}\) is neither subset nor superset of \(J_0\).
+Recall that there is no relation between the holes of \(A\) and \(A_0\) because \(J = \mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}\) is neither subset nor superset of \(J_0\).
 So looking at restricted cases where holes are related in a specific manner can help understanding the general case.
@@
 Instead of matching an effective transition to another effective transition as in the pre-simulation definition, we match an open transition to a family of covering open-transitions.
-The second part is directly the deadlock reduction requirement.
+The second part is directly the deadlock prevention requirement.
 
@@
 However we cannot talk about states in formulas.
-The solution is to expand the existential quantifier as we did in deadlock reduction, which is possible because states are finite.
+The solution is to expand the existential quantifier as we did in deadlock prevention, which is possible because states are finite.
 \nmm{R_{13} \defobject \mpar{s_1, s_3} \mapsto \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}} is a witness of the transitivity, proof is given in appendix \ref{apx:trans}.
@@
 \begin{defi}[Open automata refinement]
-For two open automata \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), ``\(A_1\) is a refinement of \(A_2\) looking at \(H\)", noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), is defined as:
+For two open automata \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a refinement of \(A_2\) looking at \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), is defined as:
 \begin{multline*}
@@
 		\quad \mpar{\forall x \in X, J'_{2x} \cap J_1 \cap H = J'_1 \cap J_2 \cap H} \\[-10pt]
-		\quad \wedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
 			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2 \cap H} \beta_{1j} = \beta_{2xj} \\
@@
 We could have defined the non-locking composition so that this is considered as an intended deadlock, making the requirement symetric.
-However the the semantics of composition in a hole is assymetric and the considered specification -as in the deadlock reduction- is the parent automaton.
+However the the semantics of composition in a hole is assymetric and the considered specification -as in the deadlock prevention- is the parent automaton.
 A symetric version of composition on a flat model of open automata is presented in Section ???\marginpar{TODO LATER}.
@@
 \end{multline}
-\[ \iff \]
+\[ \bigsymb{\iff} \]
 \begin{multline}
@@
 \item[\(\eqref{eq:drWD}\Rightarrow\eqref{eq:drID}\):]
-	Let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \(\sigma: V_1 \uplus V_2 \to \values\) be such that:
+	Let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \(\sigma: V_1 \uplus V_2 \to \values\) such that:
 	\[ \sigma \vdash R\mpar{s_1, s_2} \hyp{1} \]
@@
 	\[ \sigma \uplus \nu \vdash \fguard{t_2} \hyp{2'} \]
-	\(R\) satisfies \eqref{eq:drWD} with the current value of \(\mpar{s_1, s_2}\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \(\biguplus_{t_2 \in \fOT{s_2}} \fguard{t_2}\) so we have:
+	\(R\) satisfies \eqref{eq:drWD} with the current value of \(\mpar{s_1, s_2}\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \(\biguplus_{t_2 \in \fOT{s_2}} \fvars{\fguard{t_2}}\) so we have:
 	\[ \sigma \uplus \nu \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{3} \]
-	The \(\vdash\) hides an implicit \(\exists\) that we use to get values to the variables in \(\biguplus_{t_1 \in \fOT{s_1}}\) in a valuation \(\mu\).
+	The \(\vdash\) hides an implicit \(\exists\) that we use to get values to the variables in \(\biguplus_{t_1 \in \fOT{s_1}} \fvars{\fguard{t_1}}\) in a valuation \(\mu\).
 	The left side of the implication is proved using \hyp{1} and \hyp{2'} for the branch \(t_2\) of the disjunction.
@@
 	The left part of the implication is \hyp{1} and \hyp{3'}, so we get \(t'_2 \in \fOT{s_2}\), \(\nu': \fvars{t_2} \to \values\) and:
-	\[ \sigma \uplus \mu \uplus \nu' \vdash \alpha_1 = \alpha'_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J''_2} \beta_{1j} = \beta'_{2j} \wedge g'_2 \wedge R\mpar{s'_1, s''_2}\psubst{\psi_1 \uplus \psi'_2} \hyp{target} \]
+	\[ \sigma \uplus \mu \uplus \nu' \vdash \alpha_1 = \alpha'_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J''_2} \beta_{1j} = \beta'_{2j} \wedge g'_2 \wedge R\mpar{s'_1, s''_2}\psubst{\psi_1 \uplus \psi'_2} \hyp{4} \]
 	The witnesses for \goal{1} are \(t'_2\) and \(t_1\), and the rest is proved with a combination of \hyp{target} and \hyp{3'}.
@@
 	We can admit the left part of the implication in which we decompose the big disjunction to get \(t_2 \in \fOT{s_2}\) and:\\
-	\begin{minipage}{0.5\textwidth}\[ \sigma \vdash R\mpar{s_1, s_2} \hyp{4} \]\end{minipage}
-	\begin{minipage}{0.5\textwidth}\[ \sigma \vdash \fguard{t_2} \hyp{5} \]\end{minipage}
+	\begin{gather}
+		\sigma \vdash R\mpar{s_1, s_2} \hyp{5} \\
+		\sigma \vdash \fguard{t_2} \hyp{6}
+	\end{gather}
 	We are left to prove:
 	\[ \sigma \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{2'} \]
-	To do that we use \eqref{eq:drID} with the current value of \(\mpar{s_1, s_2}\) and \(\sigma\), and prove the premisse of the implication with \hyp{4} to get:
+	To do that we use \eqref{eq:drID} with the current value of \(\mpar{s_1, s_2}\) and \(\sigma\), and prove the premisse of the implication with \hyp{5} to get:
 	\begin{multline}
@@
 		\bigsymb{\exists} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_1} \uplus \fvars{t_2} \to \values, \\
-		\sigma \uplus \nu \vdash g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \hyp{6}
+		\sigma \uplus \nu \vdash g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \hyp{7}
 	\end{multline}
-	The left part of the implication is proved for \(t_2\) and \(\sigma\) (for the values covered by \(\nu\)) with \hyp{5}.
+	The left part of the implication is proved for \(t_2\) and \(\sigma\) (for the values covered by \(\nu\)) with \hyp{6}.
 	The right part gives \(t_1\), \(t'_2\) and \(\nu\) such that (only the interesting part of the conjunction has been extracted):
-	\[ \sigma \uplus \nu \vdash \fguard{t_1} \hyp{7} \]
+	\[ \sigma \uplus \nu \vdash \fguard{t_1} \hyp{8} \]
 	Which proves \goal{2'} with the values of \(\nu\) for the variables of \(\fguard{t_1}\) and dummy values for the other guards.
@@
 \[ V_1 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash R_{13}\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{1} \]
-\begin{description}
-	\item[\goal{0}:] Let \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}}. % TODO: quantify on s_2
-	We have the hypotheses on \(R_{12}\) and \(R_{23}\), then the current goal:
-	\[
+\item[\goal{0}:] Let \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}}.
+For every \(s_2 \in S_2\) we have the hypotheses on \(R_{12}\) and \(R_{23}\):
+\begin{gather}
 	\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
-		\quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
-		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R_{12}\mpar{s_1, s_2} \wedge g_1 \Rightarrow \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\!\!\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
+	\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{s2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
+	\quad \mpar{\forall x \in X, J'_{s2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
+	\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R_{12}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+		\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{s2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
 		\nwedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}\!\!}
-		\end{array} \hyp{0}
-	\]\[
+	\end{array}}
+	\end{array} \hyp{0} \\
 	\everymath{\displaystyle}\begin{array}{l}
@@
 	\quad \mpar{\forall x \in X, J'_{3x} \cap J_2 = J'_2 \cap J_3} \\[-10pt]
-		\nwedge V_2 \uplus V_3 \uplus \fvars{t_2} \vdash R_{23}\mpar{s_2, s_3} \wedge g_2 \Rightarrow \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\!\!\begin{array}{l}
+	\nwedge V_2 \uplus V_3 \uplus \fvars{t_{s2}} \vdash R_{23}\mpar{s_2, s_3} \wedge g_2 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
 		\alpha_2 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x} \cap J_2} \beta_{2j} = \beta_{3xj} \\[12pt]
 		\nwedge g_{3x} \wedge R_{23}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
-		\end{array}\!\!}
+	\end{array}}
 	\end{array} \hyp{1}
-	\]\[
+\end{gather}
+And the current goal is:
+\[
 	\everymath{\displaystyle}\begin{array}{l}
 	\bigsymb{\exists} \mpar{t_{3x} \defobject \OTx{3}{x}{3x}{3x} \in \fOT{s_3}}^{x \in X}, \mpar{\forall x \in X, J'_{3x} \cap J_1 = J'_1 \cap J_3} \\[-4pt]
-		\nwedge V_1 \uplus V_3 \uplus \fvars{t_1} \vdash R_{13}\mpar{s_1, s_3} \wedge g_1 \Rightarrow \!\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\!\!\begin{array}{l}
+	\nwedge V_1 \uplus V_3 \uplus \fvars{t_1} \vdash R_{13}\mpar{s_1, s_3} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
 		\alpha_1 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x} \cap J_1} \beta_{1j} = \beta_{3xj} \\[12pt]
 		\nwedge g_{3x} \wedge R_{13}\mpar{s'_1, s'_{3x}}\psubst{\psi_1 \uplus \psi_{3x}}
-		\end{array}\!\!}
+	\end{array}}
 	\end{array} \goal{0'}
 \]
-	We use hypothesis \hyp{0} with \(t_1\) to get
+We use hypothesis \hyp{0} with \(t_1\) for every \(s_2 \in S_2\) to get
 \begin{gather*}
-		\mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X} \\
-		\mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \hyp{0'} \\
-		V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R_{12}\mpar{s_1, s_2} \wedge g_1 \Rightarrow \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+	\mpar{t_{s2x} \defobject \OT{s_2}{s'_{s2x}}{\alpha_{s2x}}{\beta_{s2xj}^{j \in J'_{s2x}}}{g_{s2x}}{\psi_{s2x}} \in \fOT{s_2}}^{x \in X_{s2}} \\
+	\mpar{\forall x \in X, J'_{s2x} \cap J_1 = J'_1 \cap J_2} \hyp{0'} \\
+	V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R_{12}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X_{s2}} \mpar{\everymath{\displaystyle}\begin{array}{l}
+		\alpha_1 = \alpha_{s2x} \wedge \bigwedge_\subbox{j \in J'_{s2x} \cap J_1} \beta_{1j} = \beta_{s2xj} \\[12pt]
+		\nwedge g_{s2x} \wedge R_{12}\mpar{s'_1, s'_{s2x}}\psubst{\psi_1 \uplus \psi_{s2x}}
 	\end{array}} \hyp{0"}
 \end{gather*}
-	Then use \hyp{1} with every \(t_{2x}\) to get
+Then use \hyp{1} with every \(t_{s2x}\) to get
 \begin{gather*}
-		\mpar{t_{3xy} \defobject \OTx{3}{xy}{3xy}{3xy} \in \fOT{s_3}}^{y \in Y_x} \\
-		\mpar{\forall y \in Y_x, J'_{3xy} \cap J_2 = J'_{2x} \cap J_3} \hyp{1x} \\
-		V_2 \uplus V_3 \uplus \fvars{t_{2x}} \vdash R_{23}\mpar{s_2, s_3} \wedge g_{2x} \Rightarrow \operatorname*{\bigsymb{\bigvee}}_{y \in Y_x} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{2x} = \alpha_{3xy} \wedge \bigwedge_\subbox{j \in J'_{3xy} \cap J_2} \beta_{2xj} = \beta_{3xyj} \\[12pt]
-			\nwedge g_{3xy} \wedge R_{23}\mpar{s'_{2x}, s'_{3xy}}\psubst{\psi_{2x} \uplus \psi_{3xy}}
-		\end{array}} \hyp{1x'}
+	Z_{s2x} \defobject \mbrc{s_2} \times \mbrc{x} \times Y_{s2x} \\
+	\mpar{t_{3z} \defobject \OTx{3}{z}{3z}{3z} \in \fOT{s_3}}^{z \in Z_{s2x}} \\
+	\mpar{\forall z \in Z_{s2x}, J'_{3z} \cap J_2 = J'_{s2x} \cap J_3} \hyp{1x} \\
+	V_2 \uplus V_3 \uplus \fvars{t_{s2x}} \vdash R_{23}\mpar{s_2, s_3} \wedge g_{s2x} \Rightarrow \operatorname*{\bigsymb{\bigvee}}_\subbox{z \in Z_{s2x}} \mpar{\!\everymath{\displaystyle}\begin{array}{l}
+		\alpha_{s2x} = \alpha_{3z} \wedge \bigwedge_\subbox{j \in J'_{3z} \cap J_2} \beta_{s2xj} = \beta_{3zj} \\[12pt]
+		\nwedge g_{3z} \wedge R_{23}\mpar{s'_{s2x}, s'_{3z}}\psubst{\psi_{s2x} \uplus \psi_{3z}}
+	\end{array}\!} \hyp{1x'}
 \end{gather*}
-	We pose \(Z \defobject \mset{\mpar{x, y}}{x \in X, y \in Y_x}\).
-	We will prove \goal{0'} for the family \(t_{3xy}^{\mpar{x, y} \in Z}\).
+We pose \nmm{Z \defobject \biguplus_{s_2 \in S_2} \biguplus_{x \in X_{s2}} Z_{s2x}}.
+We will prove \goal{0'} for the family \(t_{3z}^{z \in Z}\).
 The new goals are:
 \begin{gather}
-		\forall \mpar{x, y} \in Z, J'_{3xy} \cap J_1 = J'_1 \cap J_3 \goal{2} \\
-		V_1 \uplus V_3 \uplus \fvars{t_1} \vdash R_{13}\mpar{s_1, s_3} \wedge g_1 \Rightarrow \hspace{-3mm}\operatorname*{\bigsymb{\bigvee}}_{\mpar{x, y} \in Z}\!\!\mpar{\!\!\everymath{\displaystyle}\begin{array}{l}
-			\alpha_1 = \alpha_{3xy} \wedge \bigwedge_\subbox{j \in J'_{3xy} \cap J_1} \beta_{1j} = \beta_{3xyj} \\[12pt]
-			\nwedge g_{3xy} \wedge R_{13}\mpar{s'_1, s'_{3xy}}\psubst{\psi_1 \uplus \psi_{3xy}}
-		\end{array}\!\!} \goal{3}
+	\forall z \in Z, J'_{3z} \cap J_1 = J'_1 \cap J_3 \goal{2} \\
+	V_1 \uplus V_3 \uplus \fvars{t_1} \vdash R_{13}\mpar{s_1, s_3} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{z \in Z} \mpar{\everymath{\displaystyle}\begin{array}{l}
+		\alpha_1 = \alpha_{3z} \wedge \bigwedge_\subbox{j \in J'_{3z} \cap J_1} \beta_{1j} = \beta_{3zj} \\[12pt]
+		\nwedge g_{3z} \wedge R_{13}\mpar{s'_1, s'_{3z}}\psubst{\psi_1 \uplus \psi_{3z}}
+	\end{array}} \goal{3}
 \end{gather}
-	For \goal{2} the proof depends on \(\triangle\).
+\item[\goal{2}:] Case on \(\triangle\):
 \begin{itemize}
@@
 	\begin{align*}
-		J'_{3xy} \cap J_1 & \subseteq J'_{3xy} \cap J_2 & \text{by } & J_1 \subseteq J_2 \\
+	J'_{3z} \cap J_1 & \subseteq J'_{3z} \cap J_2 & \text{by } & J_1 \subseteq J_2 \\
 		& \subseteq J'_{2x} \cap J_3 & \text{by } & \text{\hyp{1x}} \\
-			& \subseteq J'_{2x} \cap J_3 \cap J_1 & \text{by } & J'_{3xy} \cap J_1 \subseteq J_1 \\
+		& \subseteq J'_{2x} \cap J_3 \cap J_1 & \text{by } & J'_{3z} \cap J_1 \subseteq J_1 \\
 		& \subseteq J'_{2x} \cap J_1 && \\
@@
 		& \subseteq J'_{2x} \cap J_3 & \text{by } & J_1 \subseteq J_3 \\
-			& \subseteq J'_{3xy} \cap J_2 & \text{by } & \text{\hyp{1x}} \\
-			& \subseteq J'_{3xy} \cap J_2 \cap J_1 & \text{by } & J'_1 \subseteq J_1 \\
-			& \subseteq J'_{3xy} \cap J_1 &&
+		& \subseteq J'_{3z} \cap J_2 & \text{by } & \text{\hyp{1x}} \\
+		& \subseteq J'_{3z} \cap J_2 \cap J_1 & \text{by } & J'_1 \subseteq J_1 \\
+		& \subseteq J'_{3z} \cap J_1 &&
 	\end{align*}
@@
 		& \subseteq J'_{2x} \cap J_3 && \\
-			& \subseteq J'_{3xy} \cap J_2 & \text{by } & \text{\hyp{1x}} \\
-			& \subseteq J'_{3xy} \cap J_1 & \text{by } & J_1 \supseteq J_2
+		& \subseteq J'_{3z} \cap J_2 & \text{by } & \text{\hyp{1x}} \\
+		& \subseteq J'_{3z} \cap J_1 & \text{by } & J_1 \supseteq J_2
 	\end{align*}
 	\begin{align*}
-		J'_{3xy} \cap J_1 & = J'_{3xy} = J'_{3xy} \cap J_2 & \text{by } & J_1 \supseteq J_2 \supseteq J_3 \supseteq J'_{3xy} \\
+	J'_{3z} \cap J_1 & = J'_{3z} = J'_{3z} \cap J_2 & \text{by } & J_1 \supseteq J_2 \supseteq J_3 \supseteq J'_{3z} \\
 		& = J'_{2x} \cap J_3 & \text{by } & \text{\hyp{1x}} \\
@@
 		& \subseteq J'_1 \cap J_2 & \text{by } & \text{\hyp{0'}} \\
-			& \subseteq J'_1 \cap J_2 \cap J_3 & \text{by } & J'_{3xy} \subseteq J_3 \\
+		& \subseteq J'_1 \cap J_2 \cap J_3 & \text{by } & J'_{3z} \subseteq J_3 \\
 		& \subseteq J'_1 \cap J_3 &&
@@
 \end{itemize}
-	Now the proof for \goal{3}.
-	Let \(\sigma_1: V_1 \uplus \fvars{t_1} \to \values\) and \(\sigma_3: V_3 \to \values\).
-	We use dummy values for variables in \nmm{\biguplus_\subbox{\mpar{x, y} \in Z} \fvars{t_{3xy}}} to get the left side of this implication as an hypothesis (independant from these values):
+\item[\goal{3}:] Let \(\sigma_1: V_1 \uplus \fvars{t_1} \to \values\) and \(\sigma_3: V_3 \to \values\).
+We use dummy values for variables in \nmm{\biguplus_\subbox{z \in Z} \fvars{t_{3z}}} to get the left side of this implication as an hypothesis (independant from these values):
 \[ \sigma_1 \uplus \sigma_3 \vdash R_{13}\mpar{s_1, s_3} \wedge g_1 \hyp{2} \]
-	Hypothesis that we immediately break down into:
+Hypothesis that we immediately break down into
+\begin{gather*}
+	\sigma_2: V_2 \to \values \quad s_2 \in S_2 \\
+	\sigma_1 \uplus \sigma_2 \uplus \sigma_3 \vdash R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \hyp{2'} \\
+	\sigma_1 \vdash g_1 \hyp{2"}
+\end{gather*}
+We can use immediately \hyp{0"} with valuation \(\sigma_1 \uplus \sigma_2\) to get \nmm{\nu_2: \biguplus_{x \in X} \fvars{t_{2x}} \to \values}.
+The left side of the implication is proved with the right side of \hyp{2'} and \hyp{2"}, so we get \(x \in X_{s2}\) and the hypotheses
 \begin{align}
-		\sigma_2 & : V_2 \to \values &
-		\sigma_1 \uplus \sigma_2 \uplus \sigma_3 & \vdash R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \hyp{2'} \\
-		&& \sigma_1 & \vdash g_1 \hyp{2"}
+	\sigma_1 \uplus \sigma_2 \uplus \nu_2 & \vdash \alpha_1 = \alpha_{s2x} \hyp{3a} \\
+	\sigma_1 \uplus \sigma_2 \uplus \nu_2 & \vdash \bigwedge_\subbox{j \in J'_1 \cap J'_{s2x}} \beta_{1j} = \beta_{s2xj} \hyp{3b} \\
+	\sigma_2 \uplus \nu_2 & \vdash g_{s2x} \hyp{3c} \\
+	\sigma_1 \uplus \sigma_2 \uplus \nu_2 & \vdash R\mpar{s'_1, s'_{s2x}}\psubst{\psi_1 \uplus \psi_{s2x}} \hyp{3d}
 \end{align}
-	We can use immediately \hyp{0"} with valuation \(\sigma_1 \uplus \sigma_2\) to get \nmm{\nu_2: \biguplus_{x \in X} \fvars{t_{2x}} \to \values}.
-	The left side of the implication is proved with the right side of \hyp{2'} and \hyp{2"}, so we get \(x \in X\) and the hypotheses
+We can now use \hyp{1x'} with valuation \(\sigma_2 \uplus \nu_2 \uplus \sigma_3\) to get \nmm{\nu_3: \biguplus_{Z \in Z_{s2x}} \fvars{t_{3z}} \to \values}.
+The left side of the implication is proved with the left side of \hyp{2'} and \hyp{2"}, so we get \(z \in Z_{s2x}\) and the hypotheses
 \begin{align}
-		\sigma_1 \uplus \sigma_2 \uplus \nu_2 & \vdash \alpha_1 = \alpha_{2x} \hyp{3a} \\
-		\sigma_1 \uplus \sigma_2 \uplus \nu_2 & \vdash \bigwedge_\subbox{j \in J'_1 \cap J'_{2x}} \beta_{1j} = \beta_{2xj} \hyp{3b} \\
-		\sigma_2 \uplus \nu_2 & \vdash g_{2x} \hyp{3c} \\
-		\sigma_1 \uplus \sigma_2 \uplus \nu_2 & \vdash R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \hyp{3d}
+	\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3 & \vdash \alpha_{s2x} = \alpha_{3z} \hyp{4a} \\
+	\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3 & \vdash \bigwedge_\subbox{j \in J'_{s2x} \cap J'_{3z}} \beta_{s2xj} = \beta_{3zj} \hyp{4b} \\
+	\sigma_3 \uplus \nu_3 & \vdash g_{3z} \hyp{4c} \\
+	\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3 & \vdash R\mpar{s'_{s2x}, s'_{3z}}\psubst{\psi_{s2x} \uplus \psi_{3z}} \hyp{4d}
 \end{align}
-	We can now use \hyp{1x'} with valuation \(\sigma_2 \uplus \nu_2 \uplus \sigma_3\) to get \nmm{\nu_3: \biguplus_{y \in Y_x} \fvars{t_{3xy}} \to \values}.
-	The left side of the implication is proved with the left side of \hyp{2'} and \hyp{2"}, so we get \(y \in Y_x\) and the hypotheses
+Finally to prove \goal{3} with valuation \(\nu_3\) for the implicit \(\exists\), we admit the left side of the implication choose to prove the branch \(z\):
 \begin{align}
-		\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3 & \vdash \alpha_{2x} = \alpha_{3xy} \hyp{4a} \\
-		\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3 & \vdash \bigwedge_\subbox{j \in J'_{2x} \cap J'_{3xy}} \beta_{2xj} = \beta_{3xyj} \hyp{4b} \\
-		\sigma_3 \uplus \nu_3 & \vdash g_{3xy} \hyp{4c} \\
-		\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3 & \vdash R\mpar{s'_{2x}, s'_{3xy}}\psubst{\psi_{2x} \uplus \psi_{3xy}} \hyp{4d}
-	\end{align}
-	Finally to prove \goal{3} with valuation \(\nu_3\) for the implicit \(\exists\), we admit the left side of the implication choose to prove the branch \(\mpar{x, y}\):
-	\begin{align}
-		\sigma_1 \uplus \sigma_3 \uplus \nu_3 & \vdash \alpha_1 = \alpha_{3xy} \goal{3a} \\
-		\sigma_1 \uplus \sigma_3 \uplus \nu_3 & \vdash \bigwedge_\subbox{j \in J'_{3xy} \cap J_1} \beta_{1j} = \beta_{3xyj} \goal{3b} \\
-		\sigma_3 \uplus \nu_3 & \vdash g_{3xy} \goal{3c} \\
-		\sigma_1 \uplus \sigma_3 \uplus \nu_3 &\vdash R_{13}\mpar{s'_1, s'_{3xy}}\psubst{\psi_1 \uplus \psi_{3xy}} \goal{3d}
+	\sigma_1 \uplus \sigma_3 \uplus \nu_3 & \vdash \alpha_1 = \alpha_{3z} \goal{3a} \\
+	\sigma_1 \uplus \sigma_3 \uplus \nu_3 & \vdash \bigwedge_\subbox{j \in J'_{3z} \cap J_1} \beta_{1j} = \beta_{3zj} \goal{3b} \\
+	\sigma_3 \uplus \nu_3 & \vdash g_{3z} \goal{3c} \\
+	\sigma_1 \uplus \sigma_3 \uplus \nu_3 &\vdash R_{13}\mpar{s'_1, s'_{3z}}\psubst{\psi_1 \uplus \psi_{3z}} \goal{3d}
 \end{align}
@@
 \goal{3c} is exactly \hyp{4c}.
-	\goal{3d} % TODO: branch s_2
+We prove \goal{3d} with valuation \(\mpar{\sigma_2 \uplus \nu_2}\psubst{\psi_{s2x}}\) for the branch \(s_2\):
+\begin{multline*}
+	\mpar{R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}}\psubst{\psi_1 \uplus \psi_{3z}}\psubst{\mpar{\sigma_2 \uplus \nu_2}\psubst{\psi_{s2x}}} \\
+	= R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} % TODO
+\end{multline*}
 \item[\goal{1}:] Let \(\sigma_1: V_1 \to \values\) and \nmm{\sigma_3: V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \to \values}.
@@
 Finally we can prove \goal{1'} with valuation \(\nu_1\) for the implicit \(\exists\) by admitting the left side of the implication and using \hyp{5'} for the right side.
-\end{description}
 \end{proof}

### 2021-06-02 2021-PNet-examples/PNETExamples.tex
Create PNETExamples.tex

% !TEX TS-program = pdflatex
% !TeX spellcheck = en_GB

%\documentclass{llncs}
%\usepackage[T1]{fontenc}
%\usepackage{geometry}                
%\geometry{a4paper,scale=0.8}

\documentclass[twoside]{article}
\usepackage[a4paper]{geometry}
%\usepackage[latin1]{inputenc} 
\usepackage[T1]{fontenc}

\usepackage{comment}
\usepackage{graphicx}
\usepackage{DotArrow}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{algorithm} 
\usepackage{amsfonts}
\usepackage{stmaryrd}
\usepackage{mathtools,mathpartir}
\usepackage{proof}
\usepackage{amsmath,amssymb,amscd,mathrsfs}
\usepackage{epsfig,color,subfigure,enumitem}
\usepackage{macrospNets}
\usepackage[backend=bibtex,style=numeric]{biblatex}
\usepackage{wrapfig}

\definecolor{blue}{rgb}{0,0,1}
\definecolor{red}{rgb}{1,0,0}
\definecolor{darkgreen}{rgb}{0.1, 0.5, 0.1}

\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
\newcommand{\NOTE}[1]{\textcolor{blue}{\textbf{[NOTE:#1]}}}
%\newcommand{\Eric}[1]{\textcolor{blue}{#1}}
 \newcommand{\Eric}[1]{#1}
%\newcommand{\Beyond}[1]{\textcolor[RGB]{205,179,139}{#1}} 
 \newcommand{\Beyond}[1]{#1}
\newcommand{\coloncolon}{{:\hspace{-.2ex}:}}
\newcommand{\bigcupdot}{\charfusion[\mathop]{\bigcup}{\cdot}}
\newcommand{\shortotimes}{\!\otimes\!}
\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}

\makeatletter
\makeatother
\newtheorem{theorem}{Theorem}[section]
\newtheorem{property}[theorem]{Property}
\newtheorem{proof}[theorem]{Proof}
%%\newtheorem{prop}[theorem]{Proposition}
%\newtheorem{cor}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
%\newtheorem{algorithm}[theorem]{Algorithm}
%\newtheorem{remark}[theorem]{Remark}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

%\pagestyle{plain}
\addbibresource{biblio.bib}

\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\lstset{
	columns=fixed,  
	numbers=left,          
	frame=none,           
 	keywordstyle=\bfseries,     
	escapeinside=``, 
	xleftmargin=2em, 
	xrightmargin=0em, 
	aboveskip=0em, 
	framexleftmargin=2em, 
 	morekeywords={for, if, else, then, end, in, return, not, and, or, continue, break, while, function, None}, 
 	basicstyle=\small\normalfont, 
	tabsize=2,  % tab's lenth
	breaklines
}

%\begin{comment}
\usepackage{RR}
\usepackage{hyperref}
\RRNo{???}
\RRdate{ 2021}
\RRauthor{% les auteurs
Biyang  \MakeUppercase{Wang}
\thanks[ecnu]{Shanghai Key Laboratory of Trustworthy Computing, Software College, East China Normal University, Shanghai, China}\and
Eric \MakeUppercase{Madelaine}
\thanks[inria]{INRIA/I3S Kairos; Universit\'e C\^ote d'Azur, Sophia Antipolis, France}
\and
Min \MakeUppercase{Zhang}
\thanksref{ecnu}
}

\authorhead{Wang \& Madelaine \& Zhang}

\RRetitle{Example collection: pNets, OAs, Bisims}
\RRtitle{Collection d'exemples:pNets, OAs, Bisims }
\titlehead{pNets Examples}
\RRnote{KAIROS is a common team between the I3S Lab (Univ. C\^ote d'Azur and CNRS) and INRIA Sophia Antipolis M\'editerran\'ee}

\RRabstract{
    These are examples collected from our already published papers, and some more recent, from PDP'2015 to our last ongoing work. 
}

\RRresume{ % Resume en francais
%\TODO{I have updated the french def.}
%\Beyond{And we need new french abstract.}

    %\TODO{Need update the last words.}
}

\RRkeyword{Concurrent Systems, Symbolic Bisimulation, Weak Bisimulation, Open Systems, SMT Solver, Reduction, Minimization}
\RRmotcle{Syst\`emes concurrents, Bisimulation Symbolique, Bisimulation Faible, Syst\`emes ouverts, Solveur SMT, Réduction, Minimisation}

\RRprojet{Kairos}
\RCSophia % Sophia Antipolis M\'editerran\'ee
%\end{comment}

\begin{document}
\makeRR

\begin{comment}
\begin{titlepage}
\title{\vspace*{5cm} Symbolic Weak Bisimulation for Weak Open Automaton
\thanks{This work was partially funded by UCA DS4H.}}

\author{BiYang Wang\inst{1} \ Eric Madelaine\inst{2}}
\institute{
Computer Science Master/ Engineering Track - Ubinet
\\
Université Côte d'Azur, Campus SophiaTech, 930 route des Colles, BP 145, 06903 Sophia Antipolis, France 
\\
\email{superbeyondwang@gmail.com}
\and
INRIA Sophia Antipolis M\'edit\'erann\'ee, UCA, BP 93, 06902 Sophia Antipolis, France
\\
\email{eric.madelaine@inria.fr}
}
\maketitle
\end{titlepage}
\end{comment}

\date{}

\newpage
\section{Introduction}

%\Beyond{I comment Font and Capitalization.}
% \subsubsection{Font and Capitalization.} In this article, we will use italics to emphasize the terms' first show. Terms with the first word capitalized denote the special objects in the context, e.g., `Implementation' denotes the implementation in running example, `TripleSet' denotes the Triple set of bisimulation relation.

\section{Background and notations}\label{sec:notations}

This section introduces the notations we will use in this article and recalls the definition of Open Transitions, Open Automata, their Weak versions, and the corresponding bisimulations equivalences that were first defined in \cite{henrio:Forte2016,QBMZ-AVOCS18,hou:hal-02406098,ameurboulifa2020compositional}. A significant difference with the definitions in the first three references, essential for building weak open transitions, is that one of the restrictions from previous papers, stating variables should be local to a state in LTSs, was removed in the most recent work \cite{ameurboulifa2020compositional}, providing a better foundation for weak automata theory.

\subsection{Notations}

\subsubsection{Term algebra}
\label{section:term algebra}
Formally, we assume the existence of a term algebra $\AlgT$,
where $\Sigma$ is the signature of the data and action constructors. Within $\AlgT$, we distinguish a set of expressions $\AlgE$, including a set of boolean
expressions $\AlgB$ ($\AlgB\subseteq\AlgE$). We let $e_i$ range over expressions ($e_i\in\AlgE$).
On top of $\AlgE$ we build the action algebra
$\AlgA$, with $\AlgA\subseteq\AlgT,
\AlgE\cap\AlgA=\emptyset$;
naturally, action terms will use data expressions as subterms. The function $\vars(t)$ identifies the set of variables in a term $t\in\AlgT$.

We let $e_i$ range over expressions ($e_i\in\AlgE$), $a$
range over action labels, $\symb{op}$ be operators, and $x_i$ and $y_i$ range over variable names. More precisely, we consider 2 sets of variables, \emph{standard} variables that are used in expressions, and \emph{input} variables 
that appear only in parameters of communication actions. In the following grammar of action expressions, 
parameters are input variables or data expressions:
%\Beyond{Layout problem here!}
\[
\begin{array}[l]{rcl@{\quad}p{5.5cm}}
  \alpha\in\AlgA&::=&a(p_1,\ldots,p_n)&\text{action term}\\
  p_i&::=& ?x~|~e_i &\text{parameter}\\
  e_i&::=& \symb{Value}~|~x~|~\symb{op}(\symb{e}_1,..,\symb{e}_n)&\text{expression}
\end{array}
\]

$\uplus$ is the disjoint union on sets. We extend it to a disjoint union of indexed sets defined by the merge of the two sets provided they are indexed on disjoint families.
The elements of the union of two indexed sets are then accessed by using an index of one of the two joined families. An indexed family is denoted as follows: $a_i^{i\in I}$ is a family of elements $a_i$ indexed over the set $I$.

\subsubsection{Substitution}
We denote $y \gets e$ a substitution. The application of the substitution is denoted
$\subst{y\gets e}$, the operation replaces in a term all occurrences 
of the variable $y$ by the expression $e$. 
$\Post$ ranges over (indexed) sets of substitutions; $\subst{\Post}$ is the substitution that applies all the substitutions defined by $\Post$ in a parallel manner. $\otimes$ is the composition operator on substitutions, such that for any term $t$ we have: $t\subst{\Post\shortotimes\Post'} = (t\subst{\Post'})\subst{\Post}$.

For this property to be valid, even if the substitution does not operate on all variables, we define the composition operation as follows:

\[
(x_{k} \gets e_{k})^{k\in K}\shortotimes (x'_{k'}\gets e'_{k'})^{k'\in K'} 
= (x_{k}\gets e_{k}\subst{(x'_{k'}\gets e'_{k'})^{k'\in K'}})^{k\in K} \cup (x'_{k'}\gets e'_{k'})^{k'\in K''}
\]

where $K''=\{k'\in K'|x'_{k'}\not\in\{x_k\}^{k\in K}\}$.

\subsection{Equivalence between two Styles of Open Automata}
In this sub-section, we will introduce two styles of OA illustrating Strong Bisimulation equivalence between state-oriented and data-oriented versions of the same Lotos inspired operator.

\begin{figure*}[htbp]
	\centering
    \includegraphics[width=\linewidth]{XFIG/ExamplesFromLotos}
    \caption{Two Styles Examples from Lotos, \textbf{(A)} is the Action-Oriented Example, \textbf{(B)} is the Data-Oriented Example.}
    \label{Tow Styles Examples from Lotos}
\end{figure*}

Here is a variant example using the Enable operator from Lotos. The only difference from original Enable operator is turning the $\delta$ action into an observable action. We use pNets to construct this example \cite{hou:hal-02406098},  and get OAs from it. There are two different styles: the action-oriented style Figure \ref{Tow Styles Examples from Lotos}A, and the data-oriented style Figure \ref{Tow Styles Examples from Lotos}B.

In \cite{hou:hal-02406098}, we provide the open automata in Figure \ref{App B, the two open automata} as a running example for the \emph{Generate Weakest StrFH-Bisimilar} algorithm, using first the standard generation algorithm, then the optimisation algorithm.

\begin{figure}[H]
    \centering
    \label{App B, the two open automata}
    \includegraphics[width=\linewidth]{XFIG/EnableAutomata2.pdf}
    \caption{Running Example: The two open automata}
\end{figure}

\subsection{Simple Protocol}

% \TODO{you will have to explain somewhere the details of your running example, currently readers are not able to understand your raw figures...} \Beyond{Done. Comment it after review.} \Eric{DONE}

In our new paper (Biyang, Madelaine, Zhang), and the Inria Research report RR9389, we illustrate our work on weak bisimulation, using a simple communication protocol that provides safe transport of data between two processes over unsafe media. Its Specification and Implementation (`Specification' and `Implementation' denote the Running Example) are originally encoded by pNets (see \cite{ameurboulifa2020compositional}), from which we build the corresponding Open Automata.

\begin{figure}[h]
   \centerline{\includegraphics[width=0.7\linewidth]{XFIG/SimpleProt2-Spec.pdf}}
  \caption{pNet of the protocol specification}
   \label{SimpleProtCounter:SpepNet}
\end{figure}

To spare space, we only show and explain here the pNet of the Specification, in Figure \ref{SimpleProtCounter:SpepNet}. In the Specification, the pNet has only one level with two Holes (black box participant processes P and Q) and one pLTS, which describes the external behavior of the (perfect) protocol.

The actions of P, Q and pLTS (\textit{PerfectBuffer}) are synchronized by synchronization vectors. Process P tries to communicate with Q by action $\texttt{p-send(m)}$ with message data $\texttt{m}$. The protocol gets the message data by action $\texttt{in(m)}$ with assignments $\texttt{b\_ec} \gets 0, \texttt{b\_msg} \gets \texttt{m}$, where $\texttt{b\_ec}$ indicates the number of errors detected and $\texttt{b\_msg}$ represents the message payload.
% Without participants P and Q, the protocol system may failed to send message to P at any situation.
According to the last vector, the Buffer can do $\tau$ actions independently from any P's or Q's moves.
%\TODO{This sentence sounds totally wrong...}
%\Beyond{Corrected.} 
This internal move models the capability of the protocol to detect  errors: $\texttt{b\_ec}$ can increase by one unit at any time by a $\tau$ action. That is also why we can refine this system by its implementation. Finally, the protocol system passes the message and error count by action $\texttt{out(b\_m,b\_ec)}$ and Q receives them by $\texttt{q-recv(b\_m,b\_ec)}$. 
From the second and fourth vectors, P and Q can do any action they want except the meaningful actions ($\texttt{p-send}$ and $\texttt{q-recv}$) of the protocol.
%\TODO{for me, "adding vectors" is not adding constrains, but rather %adding more possible behaviors}
%\Beyond{Corrected.}

\subsection{Running Example}
% \Beyond{Have a look at this section. I add the missing part back.}\Eric{Yes, it looks good.}

%The running example is a communication protocol via unsafe intermedia (package loss) encoded by OA that allows process P and Q (Hole P and Q) to pass data. This example will help us to illustrate our ideas and algorithms through the entire paper.

%P and Q are black-box participants for the system, and we only care about two actions from each other. Process P can start the communication by action \texttt{p-send(m)} with data \texttt{m} and Process Q can receive the message from the system by action \texttt{q-recv(m,e)} with data \texttt{m} and error count \texttt{ec}. These variables in Hole may replace by certain variables in OA.

\begin{figure}[htbp]
  \centerline{\includegraphics[width=0.7\linewidth]{XFIG/OASpec}}
  \caption{Open Automaton of the protocol Specification  }
   \label{SimpleProtCounter:SpeOA}
\end{figure}

The OA in Figure \ref{SimpleProtCounter:SpeOA}, which is computed from pNet in Figure \ref{SimpleProtCounter:SpepNet}, describes the behaviour of the Specification of the communication protocol. Consider e.g. the Open Transition $\mySS_3$ from state b0 to b1, the Hole P is involved and performs action \texttt{p-send(m)}, its predicate is True, and its Post assigns variables \texttt{b\_ec} and \texttt{b\_msg}, while the resulting action visible here is \texttt{in(m)}.

% \TODO{Why the pictures go to the end of file.}
\begin{figure}[htbp]
    \centerline{\includegraphics[width=0.8\linewidth]{XFIG/OAImpl}}
    \caption{Open Automaton of the Implementation}
    \label{SimpleProtCounter:ImplOA}
\end{figure}

The OA in Figure \ref{SimpleProtCounter:ImplOA} represents the behaviour of the Implementation. In the Implementation, the system becomes more detailed and complex. The states 100, 220, 210, and their actions reflect the internal structure of the protocol. The message data and error counter pass through several variables. We do not need to pay too much attention to its mechanical details, apart from knowing it is just one of all possible implementations.

\begin{figure}[htbp]
   \centerline{\includegraphics[width=0.8\linewidth]{XFIG/WOASpec}}
   \caption{Weak Open Automaton of the Specification %\TODO{change 'formulae' to 'formulas'. And add '(n)' to WOT that have a meta var inside.}\Beyond{Done.}
   }
   \label{SimpleProtCounter:WeakSpecOA}
\end{figure}

\subsubsection{Implementation WOA}

According to Definition \ref{def:buildweakOT}, Weak OAs in Figure \ref{SimpleProtCounter:WeakSpecOA} is built from (strong) OAs from Figure \ref{SimpleProtCounter:SpeOA}; Weak OAs in Figure \ref{SimpleProtCounter:ImplWOA} is built from (strong) OAs from Figure \ref{SimpleProtCounter:ImplOA}.

According to rule $\WTUn$, each state has a Self-Loop $tau$ transition.

\begin{mathpar}
W_\tau = \openrule
{\{\}, True, ()}
{s \OTWeakarrow {\tau} s}, \forall s \in \mathcal{S}
\end{mathpar}

Then each OT can be transformed to a WOT by rule $\WTDeux$. For example, we get $\WS_1$, in Figure \ref{SimpleProtCounter:WeakSpecOA}, built from $\mySS_1$, in Figure \ref{SimpleProtCounter:SpeOA}.

\begin{mathpar}
\WS_1 = \openrule
{\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], ()}
{b0 \OTWeakarrow {\texttt{p-a}} b0}
%, \forall s \in \mathcal{S} \text{(State set of Implementation OA)}
\end{mathpar}

It's the same for $\WS_2$, $\WS_3$, $\WS_5$, $\WS_6$, and all the red arrow lines in Figure \ref{SimpleProtCounter:ImplWOA}.

Rule $\WTTrois$ is the most interesting one. Let us take $\WS_4$ as an example. We have $\mySS_4$ in Figure \ref{SimpleProtCounter:SpeOA}. This OT has the same source state and target state b1 with $\tau$ action. Nevertheless, this OT can occur infinitely, which forms a transition sequence like $\mySS_4^{*}$.

We can build a WOT, $\WS_4(2)$ from the transition sequence $\mySS_4;\mySS_4$ by rule $\WTTrois$:

\begin{mathpar}
\WS_4(2) = \openrule
    {\{\},True,( \texttt{b\_ec } \gets \texttt{b\_ec + 2})}
    {b1 \OTWeakarrow {\tau} b1}
\end{mathpar}

Then we use mathematical induction to get $\WS_4(n)$ from $\mySS_4^{*}$. Here $n$ is a natural number indicating how many times it goes through $\mySS_4$. Actually, $\WS_4(n)$ is a meta weak open transition (meta-WOT), and variable $n$ is a meta-Variable, which will be formalized in the next section (same as $\WS_3(n)$, $\WS_5(n)$, $\WS_6(n)$, $\WS_7(n)$). 
%\Beyond{Maybe we should comment the following sentence.}At that point we will show the WOA of implementation which contains many meta-WOTs.

%\TODO{There used to be an explanation somewhere of your "class of equivalent states \{000,202\}, it seems to have been lost in moving some parts...}
%\Beyond{I added a new paragraph at the end of this section. }
%\Eric{Ok, but I prefer to move it at the beginning.}
%\Beyond{Yes. Accepted.}

\begin{figure}[ht]
   \centerline{\includegraphics[width=0.8\linewidth]{XFIG/WOAImpl}}
   \caption{Weak Open Automaton of the Implementation}
   \label{SimpleProtCounter:ImplWOA}
\end{figure}

%\TODO{We will have to fight against latex floating figures, but only after everything is polished before this point, and definitely fixed} \Beyond{Yes. I like the words "Fight against". It always shows up at somewhere I don't like.}

In Figure \ref{SimpleProtCounter:ImplWOA} , there is a circle covering states 000 and 202, which means these two states are equivalent in some sense. This is because the only transition connecting 000 and 202 is $\WI_{\tau}$, and they all have \textit{similar} self-loop and outgoing transitions. In other words, the environment (observer or other components at the same or higher level of pNet) can not distinguish which state the current system visits.

Let us show some details of the weak transitions in Figure \ref{SimpleProtCounter:ImplWOA}. Most of them are also meta-WOTs. The full set of weak transitions is listed in Appendix \ref{Appendix:Details of Implementation of the Example}.

\medskip
$\WI_{456}(n)$ is constructed from the transition sequence $(\WI_4WT_5\WI_6)^{*}$.
\begin{mathpar}
\WI_{456}(n) = \openrule
         {\{\}, True, 
    (\texttt{s\_ec}\gets \texttt{s\_ec}+n)}
  {100 \OTWeakarrow {\tau} 100}, \forall n \geqslant 0
\end{mathpar}

$\WI_4$ is transformed from $\SI_4$.
\begin{mathpar}
\WI_4= \openrule
         {\{\}, True, 
   (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec}, \texttt{s\_ec}\gets \texttt{s\_ec})}
         {100 \OTWeakarrow {\tau} 210}
\end{mathpar}

$\WI_4(n)$ is constructed by transition sequence $\WI_{456}(n);\WI_4$.
It is easy to see that $\WI_4$ is a particular part of $\WI_4(n)$ when $n = 0$. So, it is enough only to keep $\WI_4(n) $ and omit $\WI_4$.

\begin{mathpar}
\WI_4(n) = \openrule
         {\{\}, True, 
   (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec}+n, \texttt{s\_ec}\gets \texttt{s\_ec}+n)}
         {100 \OTWeakarrow {\tau} 210}, \forall n \geqslant 0
\end{mathpar}

$\WI_3(n)$ is constructed by transition sequence $\WI_{\tau};\WI_3;\WI_{456}(n)$:
\begin{mathpar}
\WI_3(n) = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
    (\texttt{s\_msg}\gets \texttt{m}, \texttt{s\_ec}\gets n)}
  { \{000,202\} \OTWeakarrow {\texttt{in(m)}} 100}, \forall n \geqslant 0
\end{mathpar}

$\WI_{3a}(n)$ is constructed by transition sequence $\WI_{\tau};\WI_3;\WI_{456}(n);\WI_4$:
\begin{mathpar}
\WI_{3a}(n) = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
    (\texttt{m\_msg}\gets \texttt{m}, \texttt{m\_ec}\gets n, \texttt{s\_ec}\gets n)}
  { \{000,202\} \OTWeakarrow {\texttt{in(m)}} 210}, \forall n \geqslant 0
\end{mathpar}

For all $\tau$ transitions above, we have a similar WOT that include a non-$\tau$ move from an external action of P or Q, for example:
\begin{mathpar}
\WI_{4P}(n) = \openrule
         {\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], 
   (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec}+n, \texttt{s\_ec}\gets \texttt{s\_ec}+n)}
         {100 \OTWeakarrow {\texttt{p-a}} 210}
\end{mathpar}

Similarly, we can build all other transitions.

\subsection{Reduce the Running Example}
% \TODO{I don't know how to do it, but these figures are nearly unreadable even on my big screen, you should try to reorganize them...}
% \Beyond{I changed the layout and it's better now.}

Let us apply these three rules for the Implementation OA of our example in Figure \ref{Reduction of Implement OA}A (we don't give fresh names to variables for readability).

\begin{table}[hb]
    \centering
    \caption{Relation Triples for $IOA_2$ and $IOA_1$}
    \begin{tabular}{c c l}
		\hline
	     $IOA_2$ & $IOA_1$ & Predicate\\
	    \hline
        S1 & $000$ & True\\
        S1 & $202$ & True\\
        S4 & $100$ & $\texttt{s\_msg' = s\_msg} \land \texttt{s\_ec' = s\_ec}$\\
        S4 & $210$ & $\texttt{s\_msg' = m\_msg} \land \texttt{s\_ec' = m\_ec}$\\
        S4 & $220$ & $\texttt{s\_msg' = s\_msg} \land \texttt{s\_ec' = s\_ec}$\\
        S4 & $201$ & $\texttt{s\_msg' = r\_msg} \land \texttt{s\_ec' = r\_ec}$\\
	   	\hline
    \end{tabular}
    \label{Table:Relation Triples for IOA2 and IOA1}
\end{table}

We have $ot_{\tau}$ between two pairs of states: $\SI_\tau$ between ($202$,$000$), and $\SI_5$ between ($210$,$220$). The states in each pair have identical Self-Loop transitions. We use $\tau$-Merging in both cases getting new state $S_1$ from state pairs ($000$,$202$) and new state $S_2$ from ($220$,$210$). The rest remains the same. We get the 1st result of minimization, Figure  \ref{Reduction of Implement OA}B.

For $\SI_7$, it is the only outgoing transition from state $S_2$ and ending in state $201$. It matches the conditions for \textit{Forward Merging}. Then we can apply this rule, which merges state $S_2$ and $201$, and returns a new state $S_3$. It is the 2nd result of minimization, Figure  \ref{Reduction of Implement OA}C.

% \TODO{I don't understand the last one, in the forward merging pattern you cannot have a transition from T to S}.
% \Beyond{New conditions and pics of Merging. It can, now.}
% \TODO{Good! So you had to change the proof for the Forward merging in the appendix also...} 
% \Beyond{Yes. Done.}

\begin{table}[hbtp]
    \centering
    \caption{Relation Triples for $IOA_2$ and $\SOA$}
    \begin{tabular}{c c l}
		\hline
	     $IOA_2$ & $\SOA$ & Predicate\\
	    \hline
        S1 & b0 & True\\
        S1 & b0 & True\\
        S4 & b1 & $\texttt{s\_msg' = b\_msg} \land \texttt{s\_ec' = b\_ec}$\\
        S4 & b1 & $\texttt{s\_msg' = b\_msg} \land \texttt{s\_ec' = b\_ec}$\\
        S4 & b1 & $\texttt{s\_msg' = b\_msg} \land \texttt{s\_ec' = b\_ec}$\\
        S4 & b1 & $\texttt{s\_msg' = b\_msg} \land \texttt{s\_ec' = b\_ec}$\\
	   	\hline
    \end{tabular}
    \label{Table:Relation Triples for IOA2 and SOA}
\end{table}

We continue the processing from Figure \ref{Reduction of Implement OA}C. We find that, for $\SI_4$, it is the only transition that comes in $S_3$, apart from Self-Loop transitions. Moreover, the Self-Loop transitions are the same from state $100$ and $S_3$. We can apply rule \textit{Forward Merging} to merge the state pair ($100$,$S_3$), getting a new state $S_4$ and the third result of minimization. Then we cannot find any case that satisfies any one of our reduction rules. It is the final result.

Let us call $IOA_1$ the original Implementation OA, $IOA_2$ it's final reduced OA (Figure \ref{Reduction of Implement OA}D), and $\SOA$ the specification OA.
Even if we have not proven that forward merging preserves Weak FH-Bisimulation, we can check that indeed $IOA_1$ and $IOA_2$ are weak bisimilar, using the TripleSet in table 
\ref{Table:Relation Triples for IOA2 and IOA1}. In these triples, the primed variables are the fresh variables obtained by the successive renamings.
% \Beyond{$SOA$ has a space between S and O. Use \\SOA instead.}\Eric{Good}

%\Beyond{New table:}

\Eric{Moreover, the reduced OA is much easier to compare with the Specification OA from Figure \ref{SimpleProtCounter:SpeOA} because we have now two states matching those of the Specification OA. }
%\Eric{I propose to simplify this:}\Beyond{Let's apply $\sigma_V$ on the final reduced OA. And the variables $s
%\_msg'$ and $s\_ec'$ in Figure \ref{Reduction of Implement OA}D are same as the variables $b\_msg$ and $b\_ec$ in the Specification. 
%}\Eric{as:}

Variables in $s\_msg'$ and $s\_ec'$ in $IOA_2$ correspond to the Specification OA variables $b\_msg$ and $b\_ec$, and we can prove their equivalence using the TripleSets in Table \ref{Table:Relation Triples for IOA2 and SOA}.
% \Beyond{Accepted.}

%\TODO{What about this: \Beyond{The $IOA_2$ and $\SOA$ have Strong FH-Bisimulation relation with TripleSets in Table \ref{Table:Relation Triples for IOA2 and SOA}}.}\Eric{Well, in fact they are not, but we could change small things to make them (like what about 'r\_msg' and 'r\_ec' ?), I'm not sure we have time now. By the way, OT SS7 in Fig 1 is wrong, 'b\_m' should be 'b\_msg' I think}
% \Beyond{Yes. The bug in Spec OA is fixed.}

\begin{figure*}[ht]
	\centering
    \includegraphics[width=\linewidth]{XFIG/ReductionAllInOne}
    \caption{Minimization of the Implementation OA %\TODO{You said you would completely redraw this picture to have larger fonts in the transitions... You simplified the automata B,C,D, but did not really gain in readability. You must change the layout, maybe have only A on the first line, and change the shapes of B,C,D so that they fit in one line ?} 
    %\Beyond{Is it better now?}, \Eric{already better, still too small, try cut lines inside transition elements} \Beyond{New one! I think it's the largest font it could have. Otherwise, it will be ugly.}
    \textbf{(A)} is the original OA, \textbf{(B)} is the 1st result of Reduction, \textbf{(C)} is the 2nd result of Rection, \textbf{(D)} is the 3rd result of Reduction.}
    \label{Reduction of Implement OA}
\end{figure*}

\newpage
\printbibliography

\newpage
\appendix
\section{Details of Implementation of the Example}\label{Appendix:Details of Implementation of the Example} %\TODO{\Beyond{Need checking. I think they are fine.}}

Details of the meta-WOTs is listed here (Figure \ref{SimpleProtCounter:ImplWOA}):

In the first 3 weak transitions, $S$ denotes the set of all global states.

$ W_\tau = \openrule
{\{\}, True, ()}
{S \OTWeakarrow {\tau} S}$

$ \WI_1 = \openrule
{\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], ()}
{S \OTWeakarrow {\texttt{p-a}} S}$

$ \WI_2 = \openrule
{\{\texttt{Q}\mapsto \texttt{q-b}\}, [\forall \texttt{m,ec}. \texttt{q-b} \neq \texttt{q-recv(m,ec)} ], ()}
{S \OTWeakarrow {\texttt{q-b}} S}$

All following transitions are parametrized by an arbitrary non-negative integer $n\in \mathcal{N}$.

$ \WI_3(n) = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
    (\texttt{s\_msg}\gets \texttt{m}, \texttt{s\_ec}\gets n)}
  { \{000,202\} \OTWeakarrow {\texttt{in(m)}} 100}
$

$ \WI_{3a}(n) = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
    (\texttt{m\_msg}\gets \texttt{m}, \texttt{m\_ec}\gets n, \texttt{s\_ec}\gets n)}
  { \{000,202\} \OTWeakarrow {\texttt{in(m)}} 210}
$

$ \WI_{3b}(n) = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
    (\texttt{s\_ec}\gets n)}
  { \{000,202\} \OTWeakarrow {\texttt{in(m)}} 220}
$

$ \WI_{3c}(n) = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
    (\texttt{r\_msg}\gets \texttt{m}, \texttt{r\_ec}\gets n)}
  { \{000,202\} \OTWeakarrow {\texttt{in(m)}} 201}
$

$ \WI_4(n) = \openrule
         {\{\}, True, 
   (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec}+n, \texttt{s\_ec}\gets \texttt{s\_ec}+n)}
         {100 \OTWeakarrow {\tau} 210}
$

$ \WI_{4a}(n) = \openrule
         {\{\}, True, 
    (\texttt{s\_ec}\gets \texttt{s\_ec}+n)}
         {100 \OTWeakarrow {\tau} 220}
$

$ \WI_5(n) = \openrule
         {\{\}, True, (\texttt{s\_ec}\gets \texttt{s\_ec}+n)}
         {210 \OTWeakarrow {\tau} 220}
         $

$ \WI_{5a}(n) = \openrule
         {\{\}, True, (\texttt{s\_ec}\gets \texttt{s\_ec}+1+n)}
         {210 \OTWeakarrow {\tau} 100}
         $

$ \WI_6(n) = \openrule
         {\{\}, True, (\texttt{s\_ec}\gets \texttt{s\_ec}+1+n)}
         {220 \OTWeakarrow {\tau} 100}
         $

$ \WI_{6a}(n) = \openrule
         {\{\}, True, 
         (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec}+1+n, \texttt{s\_ec}\gets \texttt{s\_ec}+1+n)}
         {220 \OTWeakarrow {\tau} 210}
         $

% Because

% $Post_{6a}=\ post_{4}\shortotimes\ post_{456}^*\shortotimes\ post_{6}\\
% = \left( (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec})
% \shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+n) \right)
% \shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+1) \\
% = (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets (\texttt{s\_ec}+1)+n, \texttt{s\_ec}\gets (\texttt{s\_ec}+1)+n)$

\medskip
$ \WI_{456*}(n) = \openrule
         {\{\}, True, 
    (\texttt{s\_ec}\gets \texttt{s\_ec}+n)}
  {100 \OTWeakarrow {\tau} 100}
        $

$ \WI_{564*}(n) = \openrule
         {\{\}, True, 
    (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{s\_ec}\gets \texttt{s\_ec}+1+n, \texttt{m\_ec}\gets \texttt{s\_ec}+1+n)}
  {210 \OTWeakarrow {\tau} 210}
        $

$ \WI_{645*}(n) = \openrule
         {\{\}, True, 
    (\texttt{s\_ec}\gets \texttt{s\_ec}+1+n)}
  {220 \OTWeakarrow {\tau} 220}
        $

\medskip
$ \WI_7(n) = \openrule
         {\{\}, True, (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{s\_ec}+n)}
         {210 \OTWeakarrow {\tau} 201}
         $

$ \WI_{7a}(n) = \openrule
         {\{\}, True, (\texttt{r\_msg}\gets \texttt{s\_msg}, \texttt{r\_ec}\gets \texttt{m\_ec}+n+1)}
         {220 \OTWeakarrow {\tau} 201}
         $

$ \WI_{7b}(n) = \openrule
         {\{\}, True, (\texttt{r\_msg}\gets \texttt{m\_msg}, \texttt{r\_ec}\gets \texttt{s\_ec}+n)}
         {100 \OTWeakarrow {\tau} 201}
         $

$ \WI_8 = \openrule
         {\{\texttt{Q}\mapsto \texttt{q-recv(r1\_msg,r1\_ec)}\}, True, ()}
         {201 \OTWeakarrow {\texttt{out(r1\_msg,r1\_ec)}} \{202, 000\}}
         $

$ \WI_{8a}(n) = \openrule
         {\{\texttt{Q}\mapsto \texttt{q-recv(m\_msg,m\_ec}+n)\}, True, ()}
         {210 \OTWeakarrow {\texttt{out(m\_msg,m\_ec}+n)} \{202, 000\}}
         $

 $ \WI_{8b}(n) = \openrule
         {\{\texttt{Q}\mapsto \texttt{q-recv(s\_msg,s\_ec}+n+1)\}, True, ()}
         {220 \OTWeakarrow {\texttt{out(s\_msg,m\_ec}+n+1)} \{202, 000\}}
         $

 $ \WI_{8c}(n) = \openrule
         {\{\texttt{Q}\mapsto \texttt{q-recv(s\_msg,s\_ec}+n)\}, True, ()}
         {100 \OTWeakarrow {\texttt{out(s\_msg,s\_ec}+n)} \{202, 000\}}
         $

\medskip
Then for all $\tau$ transitions above we have a similar WOT that include a non-$\tau$ move from an external action of P or Q, like for example:

$ \WI_4P(n) = \openrule
         {\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], 
   (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec}+n, \texttt{s\_ec}\gets \texttt{s\_ec}+n)}
         {100 \OTWeakarrow {\texttt{p-a}} 210}
$

and

$ \WI_4Q(n) = \openrule
         {\{\texttt{Q}\mapsto \texttt{q-b}\}, [\forall \texttt{m,ec}. \texttt{q-b} \neq \texttt{q-recv(m,ec)} ],
   (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec}+n, \texttt{s\_ec}\gets \texttt{s\_ec}+n)}
         {100 \OTWeakarrow {\texttt{q-b}} 210}
$

but also e.g.:

$ \WI_{456*}P(n) = \openrule
        {\{\texttt{P}\mapsto \texttt{p-a}\}, [\forall \texttt{m}. \texttt{p-a} \neq \texttt{p-send(m)} ], 
    (\texttt{s\_msg}\gets \texttt{s\_msg}, \texttt{s\_ec}\gets \texttt{s\_ec}+n)}
  {100 \OTWeakarrow {\texttt{p-a}} 100}
        $

\bigskip
The following table give a summary of  WOTs, when sharing their names as much as possible.

\begin{table}[ht]
    \centering
    \begin{tabular}{|l|l|c|}
        \hline
        meta-WOT name & Pairs of source states and target states & \# of WOTs \\
        \hline
        $\WI_1$ $\WI_2$ $\WI_\tau$ & $\{(s,s)| s \in \texttt{States of WOA}\} \cup \{(202,000)\} $ & 21 \\
        $\WI_3(n)$ & \{(202,100),(000,100)\} & 2 \\
        $\WI_{3a}(n)$ & \{(202,210),(000,210)\} & 2 \\
        $\WI_{3b}(n)$ & \{(202,220),(000,220)\} & 2 \\
        $\WI_{3c}(n)$ & \{(202,201),(000,201)\} & 2 \\
        $\WI_4(n)$ $\WI_4P(n)$ $\WI_4Q(n)$ & \{(100,210)\} & 3 \\
        $\WI_{4a}(n)$ $\WI_4aP(n)$ $\WI_4aQ(n)$ & \{(100,220)\} & 3 \\
        $\WI_{456*}(n) $ $\WI_{456*}P(n) $ $\WI_{456*}Q(n) $ & \{(100,100)\} & 3 \\
        $\WI_5(n)$ $\WI_5P(n)$ $\WI_5Q(n)$ & \{(210,220)\} & 3 \\
        $\WI_{5a}(n)$ $\WI_{5a}P(n)$ $\WI_{5a}Q(n)$ & \{(210,100)\} & 3 \\
        $\WI_{564*}(n) $ $\WI_{564*}P(n) $ $\WI_{564*}Q(n) $ & \{(210,210)\} & 3 \\
        $\WI_6(n)$ $\WI_6P(n)$ $\WI_6Q(n)$ & \{(220,100)\} & 3 \\
        $\WI_{6a}(n)$ $\WI_{6a}P(n)$ $\WI_{6a}Q(n)$ & \{(220,210)\} & 3 \\
        $\WI_{645*}(n) $ $\WI_{645*}P(n) $ $\WI_{645*}Q(n) $ & \{(220,220)\} & 3 \\
        $\WI_7(n)$ $\WI_7P(n)$ $\WI_7Q(n)$ & \{(210,201)\} & 3 \\
        $\WI_{7a}(n)$ $\WI_{7a}P(n)$ $\WI_{7a}Q(n)$ & \{(220,201)\} & 3 \\
        $\WI_{7b}(n)$ $\WI_{7b}P(n)P$ $\WI_{7b}Q(n)$ & \{(100,201)\} & 3 \\
        $\WI_8(n)$ & \{(201,202),(201,000)\} & 2\\ 
        $\WI_{8a}(n)$ & \{(210,202),(210,000)\} & 2 \\
        $\WI_{8b}(n)$ & \{(220,202),(220,000)\} & 2 \\
        $\WI_{8c}(n)$ & \{(100,202),(100,000)\} & 2 \\

        \hline
    \end{tabular}
    \caption{All meta-WOT in the Implementation WOA}
    \label{tab:All WOT in the Implementation WOA}
\end{table}

    \bigskip

That makes a total of 73 (meta-)WOTs in the Figure \ref{SimpleProtCounter:ImplWOA}.

\newpage
\subsection{Details of the Bisimulation Checking}\label{Appendix:Details of the Bisimulation Checking}

We recall here the relation $\mathcal{R}$ that is the candidate for our meta FH-Bisimulation relation in Table \ref{tab:Bisimulation relation Triples of running example}.

\begin{table}
    \centering
    \begin{tabular}{|c|c|l|}
        \hline
        Spec state & Impl state & Predicate\\
        \hline
        b0 & $000$ & True\\
        b0 & $202$ & True\\
        b1 & $100$ & $\texttt{b\_msg = s\_msg} \land \texttt{b\_ec = s\_ec}$\\
        b1 & $210$ & $\texttt{b\_msg = m\_msg} \land \texttt{b\_ec = m\_ec}$\\
        b1 & $220$ & $\texttt{b\_msg = s\_msg} \land \texttt{b\_ec = s\_ec}$\\
        b1 & $201$ & $\texttt{b\_msg = r\_msg} \land \texttt{b\_ec = r\_ec}$\\
        \hline
    \end{tabular}
    \caption{Bisimulation relation Triples of running example}
    \label{tab:Bisimulation relation Triples of running example}
\end{table}

\bigskip
Considering the first triple <b0, 000, True>, we will prove the following properties, in which $OT<<mWOT$ means that the (strong) open transition $OT$ is covered, in the sense of Definition \ref{def:meta FH-Bisim} by the meta-WOT $mWOT$:

\bigskip
\[\begin{split}
\WS_1 << \WI_1(\emptyset) \qquad \WI_1 << \WS_1(\emptyset) \\
\WS_2 << \WI_2(\emptyset) \qquad \WI_2 << \WS_2(\emptyset) \\
\forall n \geqslant 0, n' \geqslant 0.\WS_3(n) << \WI_3(n') \\
\forall n \geqslant 0, n' \geqslant 0.\WI_3(n) << \WS_3(n')\\
\forall n \geqslant 0, n' \geqslant 0.\WI_3a(n) << \WS_3(n')\\
\forall n \geqslant 0, n' \geqslant 0.\WI_3b(n) << \WS_3(n')\\
\forall n \geqslant 0, n' \geqslant 0.\WI_3c(n) << \WS_3(n')
\end{split}
\]

%  Note: if we were using the alternative Weak bisim from Definition \ref{def:Weak-bisim}, we would have a lot more transitions to examine, as we  have 4 weak transitions for $b0$ in the specification weak automaton, but 7 WOTs from 000 in the implementation automaton.

\clearpage
\section{Examples}
In this section, we introduce some other exciting examples of Weak FH-Bisimulation (meta FH-Bisimulation) for better understanding. By lack of time, we have not yet checked the properties and equivalences of these examples.

\subsection{Integer Printer}
\label{Integer Printer}
There are two kinds of integer printer, $A(x)$ and $B(y)$, with different structure which can print any positive integer. $A(x)$ and $B(y)$ are strong automata with meta-Variable $x$ and $y$ respectively.

\begin{figure}[htbp]
	\begin{minipage}[t]{0.49\linewidth}
    \centering   
        \includegraphics[width=\linewidth]{XFIG/mA_x}
        \caption{Integer Printer A(x)}
        \label{A(x) Printer}
	\end{minipage}
	\hspace{0.01\linewidth}
	\begin{minipage}[t]{0.49\linewidth}
    \centering   
        \includegraphics[width=\linewidth]{XFIG/mB_y}
        \caption{Integer Printer B(y)}
        \label{B(y) Printer}    
	\end{minipage}
\end{figure}

And the Predicates in Table \ref{Table:Predicates of A(x) and B(y)}.

\begin{table}[hb]
    \centering
        \begin{tabular}{||c | c | c ||} 
         \hline
         A(x) & B(y) & Predicates  \\
         \hline
         <$a_0$> & <$b_0$> & $a = b = 0$\\
         \hline
         <$a_1$> & <$b_1$> & $odd(a)\land a = b+1$\\
         \hline
         <$a_1$> & <$b_2$> & $a = b$\\
         \hline
         <$a_2$> & <$b_3$> & $True$\\
         \hline
        \end{tabular}
    \caption{Predicates of A(x) and B(y)}
    \label{Table:Predicates of A(x) and B(y)}
\end{table}

It's easy to see that $Amot_0$ and $Bmot_0$ are Similar;
$Amot_2$ and $Bmot_4$ are Similar; $Amot_3$ and $Bmot_5$ are Similar.

We have a meta-WOT set $S = \Big\{mwot_2(y), mwot_{13}(y)\Big\}$ from $B(y)$, where $mwot_2(y)$ is built by $\MWTDeux$ from $Bmot_2(y)$ and $mwot_{13}(y)$ is built by $\MWTTrois$ from meta-OT sequence $Bmot_1(y);Bmot_3$:

%\TODO{to be completed} \Beyond{Done.}
\[
mwot_2(\{y\})= \openrule 
{\{\}, True, (b \gets b + 2y)} { b_0 \OTWeakarrow{\tau} b_2}
\qquad
mwot_{13}(\{y\})= \openrule
{\{\}, True, (b \gets b + 2y + 1)} { b_0 \OTWeakarrow{\tau} b_2}
\]

The proof obligation that $Amot_1(x)$ is covered by $S$ is:
\begin{mathpar}
\forall x \geqslant 0. \Big \{ \Pred_{a_0,b_0} \land True \implies \bigg[ \exists y \geqslant 0. \Big( \tau = \tau \land \Pred_{a_1,b_2}\subst{ [a \gets a + x] \uplus [b \gets b + 2y]} \Big) \\  \lor \Big( \tau = \tau \land \Pred_{a_1,b_2}\subst{ [a \gets a + x] \uplus [b \gets b + 2y + 1]} \Big) \bigg] \Big\}
\end{mathpar}

Instantiated as:

\begin{mathpar}
\forall x \geqslant 0. \Big \{ a=b=0 \implies \big[ \exists y \geqslant 0. ( \tau = \tau \land [a+x=b+2y] )   \lor ( \tau = \tau \land [a+x=b+2y+1] ) \big] \Big\}
\end{mathpar}

That is a tautology.

And $Bmot_1(y)$ and $Bmot_2(y)$ are covered by the meta-WOT built from $Amot_1(y)$.
A interesting part is that $Bmot_3$ is covered by Self-Loop $\tau$ transition built by $\MWTUn$ on state $a_1$. And its proof obligation is:
%\TODO{This is NOT updated, and incorrect. Can you update it, and give explicitly the metaWOT you use for coverage ?}
%\Eric{In fact I think the SelfLoop  you refer should rather be $Amot1;WT1(a_{1\tau})$}
%\Beyond{No. We have $Bmot_3$ starts from $b_1$ to $b_2$. And we have $Pred_{a_1,b_1}$ and $Pred_{a_1,b_2}$. So, the corresponding meta-WOT should start from $a_1$ to $a_1$. So, can't be $Amot1;WT1(a_{1\tau})$.} 
%\Beyond{Update DONE!}

%\TODO{I do not understand your answer...: the formula below is NOT updated: it contains "even(a)" that is no longer in the triples. }
%\Beyond{Well, my bad. I removed them.}

%\TODO{But I hav another problem here, The current def of meta-WOT in the journal version says that "otvars(mwot)" does NOT contain the meta-variables, only the local variables of the transitions... which one is correct ? if otvars() contains the meta variables, I may have to change the proof...}

%\Beyond{I comment my Ambiguous Long Answer. I think, $otvar$ should contain the meta-Variables. What do you think about it? And I should correct all the possible conflicts  in definitions.}
% \Beyond{This a long answer.}

% Several weeks ago, I defined the proof obligation of meta FH-Bisimulation as:\\
% $
% \forall\ otmvars(mwot).\Bigg\{ \Pred_{s,t} \land \Pred_{mwot}\implies
% \displaystyle{\bigvee_{x\in X}\bigg[\exists\ otmvars(mwot_x).
% \Big( \forall j. \gamma_{j}=\gamma_{j x}  \land \Pred_{mwot_x}}\\
% \displaystyle{
%  \land \alpha\!=\!\alpha_x \land  
%  \Pred_{s',t'_x}\subst{\Post_{mwot}\uplus\Post_{mwot_x}}\Big)\bigg]\Bigg\}}
% $

% But, you left a comment "It's OK to write $otvars$ here". So, I changed it back.
% So, I think, the $otvars$ contains the meta-Variables.

% So, in Definition meta-WOT and meta-WOA, I wrote :

% So now we have three types of variables that can occur in a meta-WOT: OA's variables from $V$ and meta-Variables from $M'$, and local variables of the OT, $otvars(mwot(M'))$.
% \Beyond{Should be: So now we have three types of variables that can occur in a meta-WOT: OA's variables from $V$ and meta-Variables from $M'$, and non-meta-Variables local variables of the OT, $otvars(mwot(M'))$.}

% We denote $otmvars(mwot(M'))=M'$, while $vars$ $(mwot(M'))$ is the set of all variables of the transition, including the automaton variables, $ot$'s local variables, as well as $ot$'s meta variables.

% Then we can redefine $otvars(mwot(M'))=vars$ $(mwot(M'))\backslash otmvars(mwot(M'))$, which will be used in the definition of meta FH-Bisimulation.\\
% ----------------\\
% I commented the last two paragraphs.

% Anyway, I reviewed your proof of Th 3 (I corrected some typos), and understand your question here.

% \Beyond{Over}

\begin{mathpar}
\forall x \geqslant 0. \bigg \{ (odd(a) \land a = b+1 \implies \Big[ \exists y \geqslant 0. \tau = \tau \land [a = b] \subst{b \gets b + 1} \Big] \bigg \}
\end{mathpar}

When $a$ is odd, then the proof obligation can be simplified as:

\begin{mathpar}
\forall x \geqslant 0. \bigg \{ a = b + 1 \implies \Big[ \exists y \geqslant 0.  a = b + 1  \Big] \bigg \}
\end{mathpar}

It's tautology.

When $a$ is even, then the proof obligation can be simplified as:

\begin{mathpar}
\forall x \geqslant 0. \bigg \{ False \implies \Big[ \exists y \geqslant 0.  a = b + 1  \Big] \bigg \}
\end{mathpar}

$False$ implies anything. So, it's tautology. As conclusion, $A(x)$ and $B(y)$ are Alt-meta FH-Bisimulation.

We derive meta-WOT from $A(x)$ as Figure \ref{mwA(x) Printer}.

% \begin{figure}[htbp]
% 	\begin{minipage}[t]{0.49\linewidth}
%     \centering   
%         \includegraphics[width=\linewidth]{XFIG/mwA_x}
%         \caption{Integer Printer A(x) of meta-WOA}
%         \label{mwA(x) Printer}
% 	\end{minipage}
% 	\hspace{0.01\linewidth}
% 	\begin{minipage}[t]{0.49\linewidth}
%     \centering
%         \includegraphics[width=\linewidth]{XFIG/mwA_x}
%         \caption{Integer Printer A(x) of meta-WOA \Beyond{meta-WOA of B(y)....}}
%         \label{mwA(x) Printer}
% 	\end{minipage}
% \end{figure}

\begin{figure}[htbp]
    \centering   
        \includegraphics[width=0.7\linewidth]{XFIG/mwA_x}
        \caption{Integer Printer A(x) of meta-WOA}
        \label{mwA(x) Printer}
\end{figure}

We have $Amwot_i, \forall i \in \{0,1,2,3\}$ come from $Amot_i, \forall i \in \{0,1,2,3\} $ (all the blue lines in Figure \ref{mwA(x) Printer} );
$
Amwot_{\tau} = 
    \openrule 
        {\{\},True,()}
        {s_0 \OTWeakarrow{\tau} s_0}, 
\forall s_0 \in \{a_0,a_1,a_2\}
$;

\begin{minipage}{0.48\linewidth}
    \begin{mathpar}
    Amwot_{10} = 
        \openrule
            {\{\}, True, (a \gets 0)}
            {a_1 \OTWeakarrow{out(a)} a_0} \\
    Amwot_{02}(\{x\}) = 
        \openrule
            {\{\}, True, (a \gets 0 + x)}
            {a_0 \OTWeakarrow{out(a)} a_2} \\
    Amwot_{21}(\{x\}) = 
        \openrule
            {\{\}, True, (a \gets 0 + x)}
            {a_2 \OTWeakarrow{\tau} a_1}
    \end{mathpar}
\end{minipage}
\hfill
\begin{minipage}{0.48\linewidth}
    \begin{mathpar}
    Amwot_{012} = 
        \openrule
            {\{\}, True, (a \gets 0)}
            {a_0 \OTWeakarrow{out(a)} a_0} \\
    Amwot_{120}(\{x\}) = 
        \openrule
            {\{\}, True, (a \gets 0 + x)}
            {a_1 \OTWeakarrow{out(a)} a_1} \\
    Amwot_{201}(\{x\}) = 
        \openrule
            {\{\}, True, (a \gets 0 + x)}
            {a_2 \OTWeakarrow{out(a)} a_2}        
    \end{mathpar}
\end{minipage}

\bigskip
This is a example where the Self-Loop Transition does not introduce a meta-Variable.

\clearpage
\subsection{Coffee Machine}
The idea of coffee vendors comes from paper \cite{BehavioralEquivalences}. It describes how a coffee vending machine works. The differences are that we have Holes, predicates, and assignments, not only action labels. So, with a little extension, we design the new specification open automaton for the vendor machine, in Figure \ref{Specification OA of Coffee Vendors}. It has two states and five actions on them. The vendor machine only has two participants, the customer named Hole P and the manager who cleans the coin box and supplies coffee named Hole M.

Customers can start the transaction, deposit coins, confirm the transaction, and withdraw the extra coins. The manager can manage the machine, supplying new coffee materials. If some customers forget to withdraw, the manager can reset the machine.

\begin{figure}[hb]
\centering   
    \includegraphics[width=\linewidth]{XFIG/CoffeeSpecOA.pdf}
    \caption{Specifications OA of Coffee Vendors}
    \label{Specification OA of Coffee Vendors}
\end{figure}

Then we design the details of the coffee vending machine system in the form of pNet, Figure \ref{pNet Implementation of Coffee Vendors}. It has two levels. The top-level organizes the cooperation of the system and customers. The bottom-level has three leaves automaton, Account, Counter, Money Box, and one Hole M, the manager.

The Account is in charge of the account of current transactions. And it only accepts coins with a face value of 1 Euro and 2 Euro. The price of coffee is 2 Euro. The Counter counts the stock of the countable coffee materials, maybe the capsules. The Money Box records the incomes since the last time the manager clean the coin box. The manager will simultaneously complete the two actions, from the system's view, clean the coin box, and supply the coffee materials (capsules) to the machine's maximum volume ($b_m$ and $m$).

\begin{figure}[htbp]
\centering   
    \includegraphics[width=0.9\linewidth]{XFIG/CoffeepNet.pdf}
    \caption{pNet Implementation of Coffee Vendors}
    \label{pNet Implementation of Coffee Vendors}
\end{figure}

Using the operational semantics of pNets, we get the implementation open automaton from the pNet. In this OA, Figure \ref{Implementations OA of Coffee Vendors}, we have a non-observable action from synchronized vectors, runout. We expect a Weak FH-Bisimulation equivalence between specification and implementation, with the relation Tripleset defined as Table \ref{Table:Bisimulation Relation Triples of Vendor Machine}.

\begin{figure}[htbp]
\centering   
    \includegraphics[width=\linewidth]{XFIG/CoffeeImplOA.pdf}
    \caption{Implementations OA of Coffee Vendors}
    \label{Implementations OA of Coffee Vendors}
\end{figure}

\begin{table}
    \centering
        \begin{tabular}{||c | l | l ||} 
         \hline
         Spec & Impl & Predicates  \\
         \hline\hline
         <b0> & <c0r0a0> & b\_m=m $\land$ b\_coin=coin $\land$ b\_n=n $\land$ b\_a=a\\
         \hline
         <b0> & <c0ra0> & b\_m=m $\land$ b\_coin=coin $\land$ b\_n=n $\land$ b\_a=a\\
         \hline
         <b1> & <c1r1a0> & b\_m=m $\land$ b\_coin=coin $\land$ b\_n=n $\land$ b\_a=a\\
         \hline
         <b1> & <c1r0a0> & b\_m=m $\land$ b\_coin=coin $\land$ b\_n=n $\land$ b\_a=a $\land$ b\_p=2\\
         \hline
        \end{tabular}
    \caption{Bisimulation Relation Triples of Vendor Machine}
    \label{Table:Bisimulation Relation Triples of Vendor Machine}
\end{table}

\newpage
\subsection{Traffic Lights}

% \TODO{Similar work? Reference and Proof.} \Beyond{Finished!}

This example is about traffic lights. Traffic lights are an appropriate use-case for real-time systems \cite{cohen2015systemverilog}. It controls a traffic light at the intersection of a busy highway and a farm road. We simplify it as a normal crossroad and abstract the timer as a Hole in pNet.

There are three kinds of lights in one traffic light, Green, Red, and Yellow. Here, the only participant is a pedestrian who should wait when the Red Light on; walk through the crossroads when Green Light on; Pay attention when the Yellow Light is illuminating. It is just like the specification in Figure \ref{Specification OA of Traffic Light}. Nevertheless, the time interval for each light is set by prior knowledge: 3s for Yellow Light, 17s for Green Light, and 20s for Red Light. With two sets of these traffic light systems controlling two directions, we can control a crossroad.

\begin{figure}[htbp]
\centering   
    \includegraphics[width=0.7\linewidth]{XFIG/TrafficLightSpecOA.png}
    \caption{Specification OA of a Traffic Light}
    \label{Specification OA of Traffic Light}
\end{figure}

Then we design the details of the traffic lights system in the form of pNet, Figure \ref{pNet Implementations of Traffic Light}. It has two levels. On the top level, it describes the cooperation between the traffic light system and pedestrians.

\begin{figure}[htbp]
\centering   
    \includegraphics[width=0.7\linewidth]{XFIG/TrafficLightpNet.png}
    \caption{pNet Implementations of Traffic Light}
    \label{pNet Implementations of Traffic Light}
\end{figure}

On the bottom level, it describes how the several components, sub-systems, work with each other. The `Light' only control which light should be on, and it will turn on another after turn off the current light; the `Controller' is in charge of communications between the other sub-systems by sending time thresholds and receive data. The `Register' is a counter which starts to count after receiving a time threshold. Furthermore, there is an ideal timer, Hole `T', which has only one action, telling it has just passed 1 second. With the help of the Hole `T', the register can count the seconds correctly.

Using the operational semantics of pNet, we get the implementation open automaton from the pNet. In this OA, Figure \ref{Implementation OA of Traffic Light}, the most interesting part is that the work of register (timer) is independent because the environment cannot observe it. The pedestrian does actions only by the signal of light.

\begin{figure}[htbp]
\centering   
    \includegraphics[width=0.9\linewidth]{XFIG/TrafficLightImpl.png}
    \caption{Implementation OA of Traffic Light}
    \label{Implementation OA of Traffic Light}
\end{figure}

The relation Triples are given like this:

\begin{table}[htbp]
    \centering
        \begin{tabular}{||c | l | l ||} 
         \hline
         Spec & Impl & Predicates  \\
         \hline\hline
         <R> & <RL51> & $c=t \land h=20$\\
         \hline
         <R> & <RL00> & $c=t \land c=h$\\
         \hline
         <G> & <GL11> & $c=t \land h=17$\\
         \hline
         <G> & <GL20> & $c=t \land c=h$\\
         \hline
         <Y> & <YL31> & $c=t \land h=3$\\
         \hline
         <Y> & <YL40> & $c=t \land c=h$\\
         \hline
        \end{tabular}
    \caption{Bisimulation Relation Triples of Traffic Lights}
    \label{Table:Bisimulation Relation Triples of Traffic Lights}
\end{table}

\clearpage

% \section{Minimization and Reduction}
% \label{Appendix:Minimization and Reduction}

% \begin{comment}
% \subsection{One State Minimization}
% \label{Appendix:proof of OSM}
% We start by proving Theorem \ref{theorem:Compress OA in one State} from section \ref{Section:Minimization and Reduction}:

% \textbf{Theorem} \ref{theorem:Compress OA in one State}
%  For any open automaton A, it and OMS(A) are strongly FH-Bisimilar.

% \medskip
% \textit{Proof} Given any open automaton, $A =< J, \mathcal{S}, s_0, V, \T > $, with One State Minimization Definition \ref{def:One State Minimization}, we get a new automaton 
% $OMS(A)= A' =< J, S'=\{ms\}, ms, V\subst{\sigma_V}\cup\{ID\}, \T' > $, that has only one state by construction.

% %\Eric{with my suggestion on Definition \ref{def:One State Minimization}, you get rid of the strange argument about non connected components of the OA (and I'm sure the theorem is true also for OA with non-connected components).
% %So you could write here:\\
% %$A' =< J, S', merged, V\cup\{ID\}, \T' > $, %and by construction you have only one state where $S'=\{merged-state\}$.}

% %\Beyond{You are right. I need to add one more procedure to merge non-connected components. So that, it fits for all OA.}

% %\TODO{Eric: check again this, I think we just don'care about non-connected components}

% %\Beyond{Yes! I need to rewrite all the proof about OMS.}
% %\Beyond{Rewrited!} \Eric{no, rewrite is an irregular verb, you have to write "rewritten" !} \Beyond{Yes, u r right. Remercier.}

% Intuitively, the Strong Bisimulation relation Triples we need is very simple, as follows:
% \begin{table}
%     \centering
%         \begin{tabular}{||c | l | l ||} 
%          \hline
%          Origin Automaton & Minimized Automaton & Predicate  \\
%          \hline\hline
%          <$s_1$> & <$ms$> & $ [\bigwedge_v^{V} v=v' ] \land ID = s_1 $\\
%          \hline
%          <$s_2$> & <$ms$> & $ [\bigwedge_v^{V} v=v' ]\land ID = s_2 $\\
%          \hline
%          <...> & <...> & ...\\
%          \hline
%          <$s_n$> & <$ms$> & $ [\bigwedge_v^{V} v=v' ]\land ID = s_n $\\
%          \hline
%         \end{tabular}
%     \caption{Relation Triples for One State Minimization}
%     \label{Table:Relation Triples for One State Minimization}
% \end{table}

% For any OT in $A$, named $OT_1$:
% \begin{mathpar}
% OT_1=
% \openrule
%  {\set{\beta},\Pred,\Post} 
%  {s_s \OTarrow {\alpha} s_t} \in \T    
% \end{mathpar}

% There exists an corresponding OT from $A'$:
% \begin{mathpar}
% OT_1'=
% \openrule
%  {\set{\beta'},Pred', Post'} 
%  {ms \OTarrow {\alpha\subst{\sigma_V}} ms} \in \T'    
% \end{mathpar}

% According to the Definition \ref{def:One State Minimization}, we have (the $J$ is the set of Hole index):
% \begin{mathpar}
% \forall j \in J.\set{\beta'_j}=\set{\beta_j}\subst{\sigma_V} \\
% Pred' = Pred\subst{\sigma_V} \land [ID = s_s] \\
% Post' = Post\subst{\sigma_V} \cup \{ID \gets s_t\} \\
% \alpha' = \alpha\subst{\sigma_V}
% \end{mathpar}

% We reason the following lemma:

% \begin{lemma}[Predicate of $\sigma_V$ effects]
% \label{lem:Predicate and Substitution}

% Predicates $\bigg [\bigwedge_v^{V} v=v' \bigg]$ just has the same effect like the substitution $\sigma_V$ ($\bigcup_v^{V} \subst{ v\gets v' } $ from Definition \ref{def:Transitions Weak Simulation}) does. Formally, we have:

% \begin{mathpar}
% \bigg [\bigwedge_v^{V} v=v' \bigg ] \implies \set{\beta_j}'^{j \in J} = \set{\beta_j}^{j \in J} ~~;~~
% \bigg [\bigwedge_v^{V} v=v' \bigg ] \implies Pred\subst{\sigma_V} = Pred\\
% \bigg [\bigwedge_v^{V} v=v' \bigg ] \implies Post\subst{\sigma_V} = Post ~~;~~
% \bigg [\bigwedge_v^{V} v=v' \bigg ] \implies \alpha' = \alpha
% \end{mathpar}
% \end{lemma}

% Then we construct the proof obligation of Strong Bisimulation:

% \begin{mathpar}
% \Pred_{s_s,ms} \land \Pred \implies 
% \displaystyle{ \forall j\in J. \set{\beta_j}\!=\!\set{\beta'_{j}} \! \land\! Pred'
%      \!\land\! \alpha\!=\!\alpha'\! \land\!  
%      \Pred_{s_t,ms}\subst{Post \uplus Post'}}
% \end{mathpar}

% With $Pred_{s_s,ms}=\bigg [\bigwedge_v^{V} v=v'  \land ID=s_s \bigg ]$ and $Pred_{s_t,ms}=\bigg [ \bigwedge_v^{V} v=v'  \land ID=s_t \bigg ]$, let's simplify it according to the Lemma \ref{lem:Predicate and Substitution}. Then, we get:

% \begin{mathpar}
% \bigg[ \bigwedge_v^{V} v=v' \land ID=s_s \bigg] \land \Pred \implies 
% \bigg ( \bigg[ \bigwedge_v^{V} v=v' \land ID=s_t \bigg ]\subst{\Post\uplus(\Post \subst{\sigma_V} \uplus \{ID\gets s_t\})} \bigg)
% \end{mathpar}

% $ID$ is new variable, formally $ID \notin V$. So, $ID \notin vars(Post)$ and the final substitution,$\subst{ID \gets s_t}$ , transforms $[ID=s_t]$ into $[s_t=s_t]$. The proof obligation is tautology.

% So, any OT from $s_s$ in $\T$ can be covered by a set of transitions from $ms$ in $\T'$.
% Symmetrically, any OT from $ms$ in $\T'$ can be covered by a set of transitions from $s_s$ in $\T$.

% % \TODO{I think you should explicit the proof obligation for the other direction, it is not the same...}
% % \Beyond{Oui, J'accepte.}

% Formally, the proof obligation goes like :

% \begin{mathpar}
% Pred_{s_s,ms} \land Pred' \implies \forall j \in J. \beta_j = \beta_j 
% \land Pred \land \alpha\!=\!\alpha \land Pred_{s_t,ms}\subst{Post \dotcup Post'}
% \end{mathpar}

% Let us simplify it according to the Lemma \ref{lem:Predicate and Substitution}. Then, we get:

% \begin{mathpar}
% \bigg [ \bigwedge_v^{V} v=v' \land ID=s_s \bigg ] \land \bigg [Pred\subst{\sigma_V} \land ID= s_s \bigg] \implies \\
% Pred \land \bigg( \bigg[\bigwedge_v^{V} v=v' \land ID=s_t \bigg]\subst{Post \uplus (Post\subst{\sigma_V} \cup \{ID \gets s_t\})}\bigg)
% \end{mathpar}

% The final substitution,$\subst{ID \gets s_t}$ , transforms $[ID=s_t]$ into $[s_t=s_t]$. The proof obligation is tautology.

% In summary, $A$ and $OSM(A)$ have strong bisimulation relation using the Tripleset in Table \ref{Table:Relation Triples for One State Minimization}.
% \end{comment}

% \subsection{Local FH-Bisimulation}
% \label{Appendix:Partial FH-Bisimulation}

% We start by formalizing a lemma about local (weak) bisimulation of a subset of open automata. This will allow us to reason locally on the states and transitions affected by reduction rules and prove they preserve the full system's bisimulation.

% Consider that we already have a system described by OA, split into two parts, local and the rest. Now consider another system where only the \emph{`local'} states and transitions are modified w.r.t those of OA, but in a way preserving the structure of states/transitions: we use for that a graph (multi-)morphism $\Phi=(\Phi^S,\Phi^T)$ so that $\Phi^S$ relates the states between the two systems, and $\Phi^T$ relates the transitions coherently, i.e.: if $ot$ is a transition from $s1$ to $s2$, then $\Phi^T(ot)$ is a transition from $\Phi^S(s1)$ to $\Phi^S(s2)$. The following Definition \ref{def:partial FH-Simulation} describes the situation.

% In general, the state mapping of these two systems can be arbitrarily 1 to n and n to 1. In this work, to validate our \emph{Reduction} approach, we only use a special case, where we have only two states in the original local-part and only one state in the reduced local part. In the Reduction, $\Phi^S$ maps two original local states to one combined new state.

% \begin{definition}[Local FH-Bisimulations]
% \label{def:partial FH-Simulation}

% Let $System= \mylangle J, \mathcal{S}, s_0, V, \T \myrangle$, and split $S$ into a \emph{`local'} subset $LocalS$ and the rest $RS$: $\mathcal{S}=LocalS\uplus RS$.

% Similarly, we split the transitions into 4 sets, local transitions $LocalOT$ are all transitions between states in $LocalS$, including Self-Loops; $incoming$ (resp. $outgoing$) are transitions from $RS$ to $LocalS$ (resp from $LocalS$ to $RS$), and $RT$ transitions between states in $RS$. Let us denote $EffectedT=LocalOT ~\uplus~ incoming ~\uplus~ outgoing$ for short. Then 
% $\T=EffectedT~\uplus~ RT$.

% Consider $System'= \mylangle J, \mathcal{S}', s_0, V, \T' \myrangle$, with:
% $\mathcal{S}'=LocalS'~\uplus~ RS$,
% $\T'=LocalOT'~\uplus~ incoming'$ $\uplus~ outgoing'~\uplus~ RT$, and we have a pair of graph multi-morphisms  
% $\Phi,\Psi$ such that:
% \begin{itemize}
%     \item $\Phi^S$ is a total surjective function on $LocalS$, formally $\forall s \in LocalS. \Phi^S(s) \subset LocalS' \land \forall s' \in LocalS'. \exists s \in LocalS. s' \in \Phi^S(s)$; and the identity (identifying elements as singletons) on the rest of the states in $RS$.
%     \item and symmetrically for $\Psi^S$, with the correspondence condition: $\forall s \in \mathcal{S}, \forall s' \in \Phi^S(s). s \in \Psi^{S'}(s')$.
% \end{itemize} 
% \end{definition}

% \begin{lemma}[Preservation by local bisimulation]
% \label{lem:Preservation by local simulation}
% Let $System$ and $System'$ be Open Auto\-mata obeying Definition \ref{def:partial FH-Simulation}, and $\Phi,\Psi$ their correspondence morphisms.

% Suppose there exists a Tripleset $\mathcal{R} = <s \in \mathcal{S},s' \in \Phi^S(s), Pred_{s,s'}>$ such that:
% \begin{itemize}
%     \item 
% for each $ot \in EffectedT$, there exists an open transition $ot'$
% with $ot' \in EffectedT'$ and $ot'.sourceState \in \Phi^S(ot.sourceState) \land ot'.targetState \in \Phi^S(ot.targetState)$, and (ot,ot') simulate each other in the sense of Definition \ref{def:Transitions Weak Simulation},
% \item symetrically, for each $ot' \in EffectedT'$, there exist an open transition $ot \in EffectedT$ with $ot.sourceState \in \Psi^S(ot'.sourceState) \land ot.targetState \in \Psi^S(ot'.targetState)$, and (ot,ot') simulate each other,
% \end{itemize}

% then $\mathcal{R}$ is a Weak FH-Bisimulation relation.

% In other terms, the transformation encoded as $\Phi$ preserves weak bisimulation on the whole system.

% \end{lemma}

% \bigskip
% %\textbf{Proof of Lemma \ref{lem:Preservation by local simulation}}

% \paragraph{Proof sketch:}

% Let $System=<J, \mathcal{S}, s_0, V, \T>$ and $System'=<J, \mathcal{S}', s_0, V, \T'>$
% obeying Definition \ref{def:partial FH-Simulation},
% $WT$ and $WT'$ the sets of weak transitions derived from $T$ and $T'$,
% and TripleSet $\mathcal{R}= <s \in \mathcal{S},s'\in \Phi^S(s), Pred_{s,s'}>$ verifying the hypotheses of Lemma \ref{lem:Preservation by local simulation}.

% According to the Definition of weak bisimulation, we need to prove:

% \begin{itemize}
% \item  For any open transition $OT$ in $\T$:
% $
% OT = \openrule
%     {\beta_j^{j\in J'},\Pred_{OT},\Post_{OT}}
%     {s \OTarrow {\alpha} s'}
% $

% there exists a set of weak open transitions $\symb{WOT}_x^{x\in X}\subseteq \WT $ 
% \begin{mathpar}
% \openrule
%     {\gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
%     {t \OTWeakarrow {\alpha_x} t'_x}
% \end{mathpar}

% such that $\forall x, \{j\in J'|\beta_j\neq\tau\}=J_{x}, (s',t_x|\Pred_{s',t'_x})\in \mathcal{R}$; 
%  and  \\

% $\Pred \land \Pred_{OT} \implies \\
% \hspace{1cm}  \quad \quad
% \displaystyle{\bigvee_{x\in X}\! 
%   \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
%      \!\land\! \alpha\!=\!\alpha_x\! \land\!  
%      \Pred_{s',t'_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}$

% \item and symmetrically any open transition from $t$ in $\T'$ can be 
%   covered by a set of weak transitions from $s$ in $\WT$.
% \end{itemize}

% Remark that we are in a restrictive case of the general condition for weak FH-Bisimulation: only a small part od system is changed between the 2 systems, and the weak simulation hypothese constrains the transition correspondence to be one to one, rather than one transition "coverd" by a set on the other side.
% So in each case, we search for a pair of open transitions, $(OT, OT')$, that simulate each other. That means there exists a $WOT'_x$ constructed from $OT'$ by rule $\WTDeux$, which fits the previous proof obligation for $OT$.  Meanwhile, there exists a $WOT_x$, which is constructed from $OT$ by rule $\WTDeux$, fits the previous proof obligation for $OT'$ with the same Triples. 
% So, the main proof idea is to prove that for all transition from $System$ there exists one transition from $System'$, keeping the same structure with morphism, that they simulate each other and vise versa. Of course, the Triple sets for the two directions will be the same.

% Let us pick out a state pair ($s1$ and $s2$), from $System$, $s1,s2 \in S$. Then we have Transition set $T_{s1,s2}(\T)$ means these OTs which start from $s1$ and ends in $s2$, formally $\forall s1,s2 \in \mathcal{S}. T_{s1,s2}(\T)=\{ot \in \T| ot~from~s1~to~s2\}$.

% \begin{proof}[Lemma \ref{lem:Preservation by local simulation}]
% \begin{figure}[htbp]
% 	\centering
%     \includegraphics[width=0.8\linewidth]{XFIG/PartialFHBisimulation}
%     \caption{Schema of partial FH-Bisimulation between two systems}
%     \label{fig:partialFHBisimulation}
% \end{figure}

% According to Definition \ref{def:partial FH-Simulation}, the Rest Part of $System$ and $System'$ don't get modified which means they are the same. Then, we can use Fig. \ref{fig:partialFHBisimulation} to show these two systems. $InStateSet \subset LocalS$,
% it contains all states which are the target state of the transitions in $incoming$. $OutStateSet \subset LocalS$,
% it contains all states which are the source state of the transitions in $outgoing$. And it's similar for $InStateSet'$ and $OutStateSet$.

% The proof will be split into 4 parts and 2 directions. Because the 2 directions of simulation are almost the same (especially with the Definition \ref{def:Transitions Weak Simulation}), we only describe one of them, from $System$ to $System'$.

% %part 1
% \bigskip
% \textbf{(1) $\forall s1,s2 \in RS$}
% \medskip

% According to Definition \ref{def:partial FH-Simulation}, binary relation $\Phi$ is a bijection for identity of states in $RS$. And the Rest Part of $System$, $System'$ are same. 
% %when $T_{s1,s2}(\T) \neq \emptyset$
% Then, of course, $\forall t \in T_{s1,s2}(\T)$, $t$ and $\Phi(t)$ are identical, and 
% $(t, \Phi(t))$ simulate each other.

% %part2
% \bigskip
% \textbf{(2) $\forall s1 \in RS \land \forall s2 \in LocalS$}
% \medskip

% When $s1 \in RS/RSOutStateSet \lor s2 \in LocalS/InStateSet$, we have $T_{s1,s2}(\T)=\emptyset$. So, we only care about the case when $s1 \in RSOutStateSet \land s2 \in InStateSet$, meaning $T_{s1,s2}(\T) = incoming$.

% Because of the morphism between $System$ and $System'$, we have:
% \begin{mathpar}
% \bigcup^{s\in InStateSet} \Phi^{S}(s) = InStateSet'
% \qquad and \qquad
% (\bigcup^{s \in S/InStateSet} \Phi^{S}(s)) \cap InStateSet' = \emptyset,\\

% \bigcup^{s\in InStateSet'} \Psi^{S'}(s) = InStateSet
% \qquad  and \qquad
% (\bigcup^{s \in S'/InStateSet'} \Psi^{S'}(s)) \cap InStateSet = \emptyset,\\

% s1' = \Phi^{S}(s1) \land \bigcup ^{s2' \in \Phi^{S}(s2)} T_{s1',s2'}(\T) = incoming' \\
% \end{mathpar}
% So we can conclude that 
% $$\forall ot \in T_{s1,s2}(\T). \forall s2' \in \Phi^{S}(s2). \exists ot' \in T_{s1,s2'}(\T'). s.t. \text{$ot'$ has the same morphism structure as $ot$}$$

% In another word, we can draw $\phi$ out of $\Phi$, which is a binary relation from $InStateSet$ to $InStateSet'$ which use all domain and co-domain. Formally, we use $\phi: InStateSet \to InStateSet'$, where $\phi \subset \Phi$. \TODO{I don't understand why you define $\phi$, you don't use it...}

% According to the hypotheses of Lemma \ref{lem:Preservation by local simulation}, $\forall ot \in EffectedT. \;\exists ot' \in EffectedT'$, $ot$ and $ot'$ simulate each other.

% Then, we have $\forall ot \in T_{s1,s2}(\T). \exists ot' \in T_{s1',s2'}(\T)$ $ot$ and $ot'$ simulate each other. That means all transitions in $incoming$ get simulated.

% %part3
% \bigskip
% \textbf{(3) $\forall s1 \in LocalS \land \forall s2 \in RS$}
% \medskip

% When $s1 \in LocalS/OutStateSet \lor s2 \in RS/RSInStateSet$, we have $T_{s1,s2}(\T)=\emptyset$. So, we only care about the case that $s1 \in OutStateSet \land s2 \in RSInStateSet$.

% Formally,
% \begin{mathpar}
% \bigcup^{\forall s1 \in RSOutStateSet. \forall s2 \in RSInStateSet} = T_{s1,s2}(\T) = outgoing
% \end{mathpar}

% Because of the morphism between $System$ and $System'$, we have:

% \begin{mathpar}
% \bigcup^{s\in OutStateSet} \Phi^{S}(s) = OutStateSet'\\
% \bigcup^{s\in OutStateSet'} \Psi^{S'}(s) = OutStateSet\\
% (\bigcup^{s \in S/OutStateSet} \Phi^{S}(s)) \cap OutStateSet' = \emptyset\\
% (\bigcup^{s \in S'/OutStateSet'} \Psi^{S'}(s)) \cap OutStateSet = \emptyset\\
% s2' = \Phi^{S}(s2) \land \bigcup ^{s2' \in \Phi^{S}(s2)} T_{s1',s2'}(\T) = outgoing' \\

% \forall ot \in T_{s1,s2}(\T). \forall s1' \in \Phi^{S}(s1). \exists ot' \in T_{s1',s2}(\T'). s.t. ot' \text{has the same morphism structure as} ot.
% \end{mathpar}

% In another word, we can draw $\phi'$ out of $\Phi$, which is a binary relation from $OutStateSet$ to $OutStateSet'$ which use all domain and co-domain. Formally, we use $\phi': OutStateSet \to OutStateSet'$, where $\phi' \subset \Phi$.

% According to Lemma \ref{lem:Preservation by local simulation}, $\forall ot \in EffectedT. \exists ot' \in EffectedT'.$ $ot$ and $ot'$ simulate each other.

% Then, we have $\forall ot \in T_{s1,s2}(\T). \exists ot' \in T_{s1',s2'}(\T)$ $ot$ and $ot'$ simulate each other. That means all transition in $outgoing$ get simulated.

% %part4
% \bigskip
% \textbf{(4) $\forall s1,s2 \in LocalS$}
% \medskip

% If $T_{s1,s2}(\T) = \emptyset$, according to morphism between $System$ and $System'$,  then $\forall s1' \in \Phi^{S}(s1).\forall s2' \in \Phi^{S}(s2).T_{s1',s2'}(\T) = \emptyset$.

% So, we only consider the case in which the states' pair contains transition.

% Formally,
% \begin{mathpar}
% \bigcup^{\forall s1.s2 \in LocalS} T_{s1,s2}(S,T) = LocalOT\\
% \forall s1,s2 \in LocalS.T_{s1,s2}(S,T) \neq \emptyset
% \end{mathpar}

% With the morphism, we have:

% \begin{mathpar}
% \forall s1' \in \Phi^{S}(s1).\forall s2' \in \Phi^{S}(s2).T_{s1',s2'}(\T) \neq \emptyset \\
% \bigcup^{\forall s1' \in \Phi^{S}(s1).\forall s2' \in \Phi^{S}(s2)}T_{s1',s2'}(\T) = LocalOT'\\
% \forall ot \in T_{s1,s2}(\T).\forall s1' \in \Phi^{S}(s1).\forall s2' \in \Phi^{S}(s2). \exists ot' \in T_{s1',s2'}(\T).\\
% s.t. \text{ $ot$ and $ot'$ has the same morphism structure.}
% \end{mathpar}

% Again, according to the hypothesis of Lemma \ref{lem:Preservation by local simulation}, $\forall ot \in EffectedT. \exists ot' \in EffectedT'$, $ot$ and $ot'$ simulate each other.

% Then, we have $\forall ot \in T_{s1,s2}(\T). \exists ot' \in T_{s1',s2'}(\T)$ $ot$ and $ot'$ simulate each other. That means all transition in $LocalOT$ get simulated.

% So far, we traverse all state pairs, which means we traverse all the transitions. Now, we have the conclusion that $\forall ot \in T, \exists ot' \in T'. s.t.$ $ot$ and $ot'$ simulate each other.

% \TODO{But this is not the end, you still have to show that they fulfill the proof obligation !}

% The other direction of proof is similar to the proof above, which concludes $\forall ot' \in T', \exists ot \in T. s.t.$ $ot$ and $ot'$ simulate each other.

% Then, the transformation encoded as $\Phi$ preserves weak bisimulation.
% \end{proof}

% \subsection{Theorems of Merging}
% \label{Appendix:Theorems of Merging}
% % \TODO{I suggest remove the word "can" here in the definition, and in all occurrences later. It's better to write "A and B simulate each other"}
% % \Beyond{Yes. Accepted.}

% \subsubsection{Tau Merging}
% \label{Appendix:Proof on tau Merging}
% % \TODO{Any reviewer reading a proof starting by "it's easy to see that" (especially if he/she has not fully memorized all your previous huge formulas, not to mention Rule WT2!) will be very upset. What makes this proof "easy", is that this particular Weak Bisimulation analysis is much simpler than the general case, because transitions correspond one to one, and the transitions themselves are mostly unchanged, so you don't need to go through detailed proof conditions on predicates and posts. But you cannot assume the reviewer will understand this by himself, you have to write it in some sufficiently formal way. I would start, at least, by giving a formal def of your "simulate each other" property. Then explain shortly why it applies easily to all pairs in the next paragraph.}

% % \Beyond{Yes. I will make it more sufficient.}

% Using the notion of \textit{Similar} in section \ref{section:Transition Merging Principles}, and the pre-conditions of $\tau$ Merging `Self-Loop transitions in $S$ and $T$ are Similar Self-Loop transitions, or $S$ and $T$ do not have Self-Loop transitions.', it is easy to see that transition in $I$ is \textit{Similar} with the transition in J (I and J can be empty set).

% The procedure of $\tau$ Merging only changes the source state and target state of transitions. So with $\bigwedge_v^{V} v=copy(v)$ in Triples, $Sin_i^{i \in I'}$ and corresponding $STin_i^{i \in I'}$ simulate each other; $Sslt_i^{i \in I}$ and corresponding $STslt_k^{k \in K}$ simulate each other;  $Tslt_i^{i \in I}$ and corresponding $STslt_k^{k \in K}$ simulate each other; $Tout_i^{i \in I'}$ and corresponding $STout_i^{i \in I'}$ simulate each other; $Tout_j^{j\in ''}$ and corresponding $STslt_j^{j \in J''}$ simulate each other.

% \begin{figure}[htbp]
% 	\begin{minipage}[t]{0.55\linewidth}
% 		\centering
%         \includegraphics[width=\linewidth]{XFIG/BeforeTauMerging.pdf}
%         \caption{Before tau Merging}
%         \label{Figure:Before tau Merging for proof}
% 	\end{minipage}
% 	\begin{minipage}[t]{0.4\linewidth}
% 		\centering
%         \includegraphics[width=\linewidth]{XFIG/AfterTauMerging.pdf}
%         \caption{After tau Merging}
%         \label{Figure:After tau Merging for proof}
% 	\end{minipage}
% \end{figure}

% \textbf{$OT\tau$ can be simulated:}
% The only thing left is that we need to find a WOT from result OA that simulates the transition $OT\tau$. It can be simulated by $tau$ transition built from rule $\WTDeux$ in the result OA.

% In $OT_\tau$, we have $\set{\beta} = \emptyset$, $\Pred = True$, $Post = \emptyset$ and $\alpha$ is a non-observable action.

% So, the proof obligation is:

% \medskip
% $
% \Pred_{s,st} \land True \!\implies\! \beta = \{\} \land True \land \underline{\alpha} = \tau \land Pred_{t,st}
% $
% \medskip

% With Triple Predicates $\Pred_{s,st} = \Pred_{t,st}$, the proof obligation is tautology.

% So, these two parts have weak bisimulation relations.

% \subsubsection{Forward Merging}
% \label{Appendix:Proof on Forward Merging}

% Just like the previous mention about $\tau$ Merging, with 
% $\bigg [\bigwedge_v^{V} v=v' \bigg]$, we know that $Sin_i^{i \in I'}$ and corresponding $STin_i^{i \in I'}$ simulate each other; $Sslt_i^{i \in I}$ and corresponding $STslt_k^{k \in K}$ simulate each other; transition in $I$ is Similar with transition in J; $Tslt_i^{i \in I}$ and corresponding $STslt_k^{k \in K}$ simulate each other; $Sout_i^{i \in I''}$ and corresponding $STout_i^{i \in I''}$ simulate each other.

% \begin{figure}[htbp]
% 	\begin{minipage}[t]{0.49\linewidth}
% 		\centering
%         \includegraphics[width=\linewidth]{XFIG/BeforeForwardMerging.pdf}
%         \caption{Before Forward Merging}
%         \label{Figure:Before Forward Merging for proof}
% 	\end{minipage}
% 	\begin{minipage}[t]{0.49\linewidth}
% 		\centering
%         \includegraphics[width=\linewidth]{XFIG/AfterForwardMerging.pdf}
%         \caption{After Forward Merging}
%         \label{Figure:After Forward Merging for proof}
% 	\end{minipage}
% \end{figure}

% This leaves us with 5 non-trivial correspondences to establish, namely
% that $STout_j^{j \in J'}$, $STslt_j^{j \in J''}$ in the result OA can be simulated; $OT$, $Tout_j^{j\in J'}$ and $Tout_j^{j \in J''}$ in original OA can be simulated.

% \bigskip\noindent
% \textbf{(1) $STout_j^{j \in J'}$ can be simulated:}
% \medskip

% Then we need to prove $STout_j^{j \in J'}$ can be simulated by a WOT, which is built from transition sequence $OT-Tout_j^{j \in J'}$. $s'$ refers to two states; one is in the original OA, which is the target state of $Tout_j^{j \in J'}$; the other is in the result OA, which is the target state of $STout_j^{j \in J'}$.
% \smallskip
% Let $WOT_j$ be the result of \textit{Forward Merging} with OT and $Tout_j$, then the proof obligation is:

% \medskip
% $\Pred_{s,st} \land STout_j.Pred \!\implies\! \\
% STout_j.\beta = WOT_j.\beta \land WOT_j.Pred \land WOT_j.Action = STout_j.Action \land Pred_{s',s'}\subst{WOT_j.Post \uplus STout_j.Post}
% $
% \medskip

% According to merging rules $\MTUn$ and construction rule $\WTTrois$, we know their Hole actions, transition actions, and predicates should be the same.

% So, the proof obligation simplifies as:

% \medskip
% $\Pred_{s,st}  \!\implies\! \Pred_{s',s'}\subst{ (Tout_j^{j \in J} \shortotimes OT.Post ) \uplus ( Tout_j^{j \in J} \shortotimes OT.Post ) }
% $
% \medskip

% With predicates $\Pred_{s,st} = \Pred_{s',s'}$ , the proof obligation is tautology.

% \bigskip\noindent
% \textbf{(2) $STslt_j^{j \in J''}$ can be simulated:}
% \medskip

% $STslt_j^{j \in J''}$ is the result of applying rule $\MTUn$ on $OT$ and transition $Tout_j^{j\in J''}$.

% \begin{minipage}[h]{0.48\linewidth}
%     \centering
%     \begin{mathpar}
%         OT = 
%         \openrule
%          {\set{\gamma}, Pred, Post} 
%          {S \OTarrow{\underline {\alpha}} T}
%      \end{mathpar}
% \end{minipage}
% \hfill
% \begin{minipage}[h]{0.48\linewidth}
%     \centering
%     \begin{mathpar}
%         Tout_j^{j \in J''} = 
%         \openrule
%          {\set{\gamma_1}, Pred_1, Post_1} 
%          {T \OTarrow{\alpha_1} S}
%     \end{mathpar}
% \end{minipage}

% \bigskip

% After applying $\MTUn$ on $OT$ and $Tout_j^{j \in J''}$, merging state $S$,$T$, applying $\sigma_V$, we get $STslt_j^{j \in J''}$ as :

% \begin{mathpar}
% \centering
%     STslt_j^{j \in J''} = 
%     \openrule
%      {(\set{\gamma}\dotcup \set{\gamma_1}\subst{\Post})\subst{\sigma_V}, 
%      (Pred \land Pred_1\subst{Post})\subst{\sigma_V}, 
%      (Post_1\shortotimes Post)\subst{\sigma_V}} 
%      {ST \OTarrow {(\alpha_1\subst{Post})\subst{\sigma_V}}\ ST}
% \end{mathpar}

% After applying $\WTTrois$ to construct a WOT from $OT$ and $Tout_j^{j \in J''}$, we get $WOT_j^{j \in J''}$:

% \begin{mathpar}
% \centering
%     WOT_j^{j \in J''} = 
%     \openrule
%      {\set{\gamma}\dotcup \set{\gamma_1}\subst{\Post}, 
%      Pred \land Pred_1\subst{Post}, 
%      Post_1\shortotimes Post} 
%      {S \OTWeakarrow{\alpha_1\subst{Post}}\ S}
% \end{mathpar}

% With predicate $\Pred_{S,ST} = \bigg [ \bigwedge_v^{V} v=v' \bigg ]$ and Lemma \ref{lem:Predicate and Substitution} , it's easy to see that the proof obligation about $STslt_j^{j \in J''}$ being simulated by $WOT_j$ is a tautology.

% \bigskip\noindent
% \textbf{(3) $Tout_j^{j \in J''}$ can be simulated:}
% \medskip

% The previous context continues. 
% A WOT which is constructed from $STslt_j^{j \in J''}$:

% \begin{mathpar}
% \centering
%     WOT_{STslt_j} = 
%     \openrule
%      {(\set{\gamma}\dotcup \set{\gamma_1}\subst{\Post})\subst{\sigma_V}, 
%      (Pred \land Pred_1\subst{Post})\subst{\sigma_V}, 
%      (Post_1\shortotimes Post)\subst{\sigma_V}} 
%      {S \OTWeakarrow {(\alpha_1\subst{Post})\subst{\sigma_V}}\ S}
% \end{mathpar}

% The proof obligation that $Tout_j^{j \in J''}$ be simulated by $WOT_{STslt_j}$:

% \bigskip
% $
% Pred_{T,ST} \land Pred_1 \implies \\
% \quad \quad  \forall j \in J. \set{\gamma_1}_j = (\set{\gamma}\dotcup \set{\gamma_1}\subst{\Post})_j\subst{\sigma_V} 
% \land \alpha_1 = (\alpha_1\subst{Post})\subst{\sigma_V} 
% \land (Pred \land Pred_1\subst{Post})\subst{\sigma_V} 
% \land Pred_{S,ST}\subst{Post \uplus (Post_1\shortotimes Post)\subst{\sigma_V}}
% $

% \bigskip
% Here, the $J$ is the set of the Hole index.
% We have $Pred_{T,ST}=\bigg [ [\bigwedge_v^{V} v=v'] \land [\bigwedge^{i \in K} [v_i = e_i]~where~ \subst{v_i \gets e_i} \in Post ] \bigg ]$.

% $\bigg [\bigwedge^{i \in K} [v_i = e_i]~where~ \subst{v_i \gets e_i} \in Post \bigg]$ just "Simulate" the effect of the substitution $Post$. So, we have:

% \medskip
% $
% \bigwedge^{i \in K} [v_i = e_i]~where~ \subst{v_i \gets e_i} \in Post \implies \alpha_1 = \alpha_1\subst{Post}
% $

% \bigskip

% And with Lemma \ref{lem:Predicate and Substitution}, we have:\
% $[\bigwedge_v^{V} v=v'] \implies \alpha_1 = (\alpha_1\subst{Post})\subst{\sigma_V}$
% \medskip

% It's the same for $Pred$ and $Post$.

% \bigskip
% Then, we have:
% $Pred_{S,ST}\subst{Post \uplus (Post_1\shortotimes Post)\subst{\sigma_V}}=[\bigwedge_v^{V} v=v']\subst{Post \uplus (Post_1\shortotimes Post)\subst{\sigma_V}}=True$
% \medskip

% With condition $\forall~holeAction \in \set{\beta} = \tau~or~empty$, we have:

% \begin{mathpar}
% \forall j \in J. \set{\gamma_1}_j = (\set{\gamma}\dotcup \set{\gamma_1}\subst{\Post})_j\subst{\sigma_V}
% \end{mathpar}

% After simplifying the proof obligation, we only need to prove:

% \begin{mathpar}
% Pred_{T,ST} \land Pred_1 \implies Pred
% \end{mathpar}

% From the pattern, we know $OT$ is the only transition that comes in $T$ (besides the Self-Loop transitions), and $Tout_j^{j\in J''}$ goes out $T$. That means only and only if the $Pred$ is $True$, then the transition flow goes through $OT$ and $Tout_j^{j\in J''}$ ($Pred_j$ also should be $True$). In other words, when we are talking about which $WOT$ can simulate $Tout_j^{j\in J''}$, the subtext is "$Pred$ is $True$". Otherwise, $Tout_j^{j\in J''}$ will never happen, and it is meaningless to simulate an open transition that would never happen.

% However, it is necessary to talk about the meaningless case, $Pred=False$. It means the $OT$ will never happen. All transitions start from $T$, these states are only available from $T$, and their transitions will never happen or be reached. In that case, the guard of $STslt_j$, $Pred\land\Pred_1\subst{Post}$, is $False$ which means $STslt_j^{j \in J''}$ will never happen. Of course, $STout_j^{j \in J'}$ will never happen. So, the reduction would not increase any possibility that the original OA does not have.

% In summary, $Tout_j^{j \in J''}$ can be simulated.

% \bigskip\noindent
% \textbf{(4) $OT$ can be simulated:}
% \medskip

% $OT$ can be simulated by a $tau$ transition built from rule $\WTDeux$. In OT, we have $\set{\beta} = \{\}$, $\Pred = True$, $Post = ()$ and $\alpha$ is a non-observable action.

% The proof obligation is:

% \medskip
% $\Pred_{s,st} \land OT.\Pred \!\implies\! \beta = \{\} \land True \land \alpha = \tau \land Pred_{t,st}\subst{OT.Post}$
% \medskip

% We have $\Pred_{t,st} =Pred_{T,ST}=\bigg [ [\bigwedge_v^{V} v=v'] \land [\bigwedge^{i \in K} [v_i = e_i]~where~ \subst{v_i \gets e_i} \in Post ] \bigg ]$

% \bigskip
% then, 
% $Pred_{t,st}\subst{OT.Post} = [ v_i = e_i]^{i \in K} \subst{v_i \gets e_i}^{i \in K} = \{ e_i = e_i\}^{i \in K}$.
% \smallskip

% With predicate $\Pred_{s,st} = [\bigwedge_v^{V} v=v']$, the simplified proof obligation should be:

% \medskip
% $OT.\Pred \!\implies\! True$
% \medskip

% The proof obligation is tautology.

% \bigskip\noindent
% \textbf{(5) $Tout_j^{j\in J'}$ can be simulated:}
% \medskip

% $Tout_j^{j\in J'}$ can be simulated by WOT from corresponding $STout_j^{j \in J'}$

% The proof obligation is:

% \medskip
% $\Pred_{t,st} \land Tout_j.\Pred \!\implies\! \\ Tout_j.\beta = STout_j.\beta \land STout_j.Pred \land Tout_j.Action = STout_j.Action \land Pred_{s',s'}\subst{Tout_j.Post \uplus STout_j.Post}$
% \medskip

% According to merging rule $\MTUn$, after merging states and applying substitution $\sigma_V$, the proof obligation becomes:

% \medskip
% $[ v_i = e_i ]^{i \in I} \land Tout_j.\Pred 
% \!\implies\!  \\
% Tout_j.\beta = (Tout_j.\beta\subst{OT.Post})\subst{\sigma_V} 
% \land (Tout_j.Pred\subst{OT.Post} \land OT.Pred )\subst{\sigma_V}
% \land Tout_j.Action = (Tout_j.Action\subst{OT.Post} )\subst{\sigma_V}
% \land \\ Pred_{s',s'}\subst{Tout_j.Post \uplus (Tout_j.Post\subst{OT.Post})\subst{\sigma_V}}$
% \medskip

% Just like the proof in \textbf{(3)}, we have:

% \medskip
% $[ v_i = e_i ]^{i \in K} \land Tout_j.\Pred \!\implies\! \\
% Tout_j.\beta = (Tout_j.\beta\subst{OT.Post})\subst{\sigma_V} 
% \land (Tout_j.Pred\subst{OT.Post})\subst{\sigma_V}  
% \land Tout_j.Action = (Tout_j.Action\subst{OT.Post})\subst{\sigma_V}$

% \medskip
% $Pred_{s',s'}\subst{Tout_j.Post \uplus (Tout_j.Post\subst{OT.Post})\subst{\sigma_V}} = True$
% \bigskip

% After simplifying the proof obligation, we only need to prove:

% \medskip
% $[ v_i = e_i ]^{i \in K} \land Tout_j.\Pred \!\implies\! 
% OT.Pred$
% \medskip

% Just like discussion in \textbf{(3)}, if $OT.Pred=False$, then $Tout_j^{j \in J'}$ would never happen, which is meaningless. When $OT.Pred=True$, the proof obligation is tautology.

% This terminates the proof for \textit{Forward Merging}.

% \subsubsection{Backward Merging}
% \label{Appendix:Proof on Backward Merging}

% The proof is similar to the previous sub-section.

\end{document}

### 2021-06-03 2021-Refinement/report.tex
Fixed proof of lemma 1

@@
 % TODO: CITER LES CONFERENCES
-% change deadlock reduction into deadlock prevention?
 
@@
 However equivalences relations are not always sufficient to perform verification, refinement relations are also used.
-For instance an example of open pNet where equivalence is not sufficient was encountered in ...\marginpar{Paper where the motivating example came up}.
+For instance an example of open pNet where equivalence is not sufficient was encountered in an article about algorithms fo weak bisimulation on open automata \cite{wang:hal-03126313}.
 
@@
 \begin{align*}
-	notation\_with\_variables & \defnotation notated\_object\_using\_the\_variables \\
-	name & \defobject fully\_defined\_mathematical\_object
+	\mathit{notation\_with\_variables} & \defnotation \mathit{notated\_object\_using\_the\_variables} \\
+	\mathit{name} & \defobject \mathit{fully\_defined\_mathematical\_object}
 \end{align*}
@@
 \end{align*}
-It is an alternative implementation of the enable operator which is FH-bisimilar to the previous one, as proved in \marginpar{probably forte, check that}.
+It is an alternative implementation of the enable operator which is FH-bisimilar to the previous one \cite{henrio:01299562}.
 Note that in this example \(r\) and \(l\) are a hole names and also closed terms: this is a naming conflict, though it is not ambiguous because \(J \cap \rterms = \emptyset\) always holds.
@@
 Intuitively it holds because the cartesian product of states, the union of sets, the union of maps and the conjunction on formulas (in the guards) are commutative and associative.
-This allows us to define the simultaneous composition \(A\psubst{A_j^{j \in J'}}\) as the result of any order of (sequential) composition where each \(A_j\) is composed in the hole \(j\).
-% psubst to pcomp macro [[]]
+This allows us to define the simultaneous composition \(A\mdbrk{A_j^{j \in J'}}\) as the result of any order of (sequential) composition where each \(A_j\) is composed in the hole \(j\).
+Even if an automaton is composed in two distinct holes it does not share its variables, each composition makes the cartesian product of states and a disjoint union of the variables.
+In practise, variables may have to be renamed.
 
@@
 Here the main expected properties are related to composition and action refinement. % LATER: explain action refinement here or remove if not tackled
-Because of composition, a relation as strong as simulation must be used as observed in the articles about FH-bisimulation \cite{henrio:01055091}.
+Because of composition, a relation as strong as simulation must be used.
 
@@
 A relation of second kind will be called ``relation on automata" whereas a relation of the first kind is called ``relation on configurations" as defined below.
-In the work on FH-bisimulation\marginpar{re-cite FH-bisim as near as the previous citation?} such a relation \(R\) was defined as triples in \(S_1 \times S_2 \times \formulas\) where for \(\mpar{s_1, s_2} \in S_1 \times S_2\) there is a unique \(f \in \formulas\) such that \(\mpar{s_1, s_2, f} \in R\).
+In the work on FH-bisimulation \cite{henrio:01055091} such a relation \(R\) was defined as triples in \(S_1 \times S_2 \times \formulas\) where for \(\mpar{s_1, s_2} \in S_1 \times S_2\) there is a unique \(f \in \formulas\) such that \(\mpar{s_1, s_2, f} \in R\).
 This is classically the definition of a function from \(S_1 \times S_2\) to \(\formulas\) so we will define it as such.
@@
 \end{defi}
+This definition translated to open automata the classical definition of simulation \marginpar{cite: Fernandez-Mounier-91-b}.
 The last formula means that for every pair of related configurations of the automaton and every possible transitions (\(\vdash g_1\)) from the first automaton, there is a possible transition (\(\vdash g_2\)) such that the produced action matches (\(\alpha_1 = \alpha_2\)), the same holes' action (\(J'_1 \cap J'_2\)) matches (\(\beta_{1j} = \beta_{2j}\)) and the target states are related after variable update.
@@
 The main goal of this section is to explain the different aspects of refinement in restricted cases so that they are not all introduced at once in the real refinement relation.
-In particular if we have a family of open automata \(A_i \defobject \OAg[i]\), \(0 \leq i \leq n\), let \(A \defobject \OAg\) be such that \(A = A_0\psubst{j_i \mapsto A_i \middle| 1 \leq i \leq n}\).
+In particular if we have a family of open automata \(A_i \defobject \OAg[i]\), \(0 \leq i \leq n\), let \(A \defobject \OAg\) be such that \(A = A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\).
 Recall that there is no relation between the holes of \(A\) and \(A_0\) because \(J = \mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}\) is neither subset nor superset of \(J_0\).
@@
 
-\section{Proof of equivalent definitions}\label{apx:lemeqd}
+\section{Proof of equivalent definitions}\label{apx:lemeqd} % TODO: disjunction branch, say where we get the value
 
@@
 	\[ \sigma \uplus \nu \vdash \fguard{t_2} \hyp{2'} \]
-	\(R\) satisfies \eqref{eq:drWD} with the current value of \(\mpar{s_1, s_2}\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \(\biguplus_{t_2 \in \fOT{s_2}} \fvars{\fguard{t_2}}\) so we have:
+	\(R\) satisfies \eqref{eq:drWD} with the current value of \(\mpar{s_1, s_2}\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \(\biguplus_{t_2 \in \fOT{s_2}} \fvars{t_2}\) so we have:
 	\[ \sigma \uplus \nu \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{3} \]
-	The \(\vdash\) hides an implicit \(\exists\) that we use to get values to the variables in \(\biguplus_{t_1 \in \fOT{s_1}} \fvars{\fguard{t_1}}\) in a valuation \(\mu\).
+	The \(\vdash\) hides an implicit \(\exists\) that we use to get values to the variables in \(\biguplus_{t_1 \in \fOT{s_1}} \fvars{t_1}\) in a valuation \(\mu\).
 	The left side of the implication is proved using \hyp{1} and \hyp{2'} for the branch \(t_2\) of the disjunction.
@@
 	\[ \sigma \uplus \nu \uplus \mu \vdash \fguard{t_1} \hyp{3'} \]
-	At this point we have a \(t_1\) and a \(t_2\) so we may think that the proof is about to be finished because the only property left to prove is:
+	At this point we have a certain \(t_1\) and \(t_2\) so we may be tempted to use them to prove the goal:
 	\begin{multline}
@@
 	\end{multline}
-	However we cannot yet prove it because we don't know whether \(t_2\) and \(t_1\) do match.
-	In order to get a \(t_2\) matching \(t_1\) we use will use \eqref{eq:drID}.
-	\eqref{eq:drID} with current value of \(\mpar{s_1, s_2}\), \(t_1\) and \(\sigma \uplus \mu\) as a valuation of \(V_1 \uplus V_2 \uplus \fvars{t_1}\) gives:
+	However we cannot yet prove it because we don't know whether \(t_2\) and \(t_1\) match.
+	In order to get a \(t_2\) matching \(t_1\) we will use the fact that \(R\) is a simulation.
+	\begin{multline}
+		\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \forall \sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values, \\
+		\mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \\
+		\sigma \uplus \nu \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \hyp{sim}
+	\end{multline}
+	\hyp{sim} with current value of \(\mpar{s_1, s_2}\), \(t_1\) and \(\sigma \uplus \mu\) as a valuation of \(V_1 \uplus V_2 \uplus \fvars{t_1}\) gives:
 	\begin{multline}
@@
 	\[ \sigma \uplus \mu \uplus \nu' \vdash \alpha_1 = \alpha'_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J''_2} \beta_{1j} = \beta'_{2j} \wedge g'_2 \wedge R\mpar{s'_1, s''_2}\psubst{\psi_1 \uplus \psi'_2} \hyp{4} \]
-	The witnesses for \goal{1} are \(t'_2\) and \(t_1\), and the rest is proved with a combination of \hyp{target} and \hyp{3'}.
+	The witnesses for \goal{1} are \(t'_2\) and \(t_1\), and the rest is proved with a combination of \hyp{4} and \hyp{3'}.
 \item[\(\eqref{eq:drWD}\Leftarrow\eqref{eq:drID}\):]
@@
 \item[\goal{1}:] Let \(\sigma_1: V_1 \to \values\) and \nmm{\sigma_3: V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \to \values}.
-We have the hypotheses on \(R_{12}\) and \(R_{23}\), then the current goal: % TODO HERE: get s_2 by decomposing R_{13}
+We have the hypotheses on \(R_{12}\) and \(R_{23}\) for a specific \(s_2\), then the current goal:
 \begin{gather}
@@
 Hypothesis that we immediately break down into:
-\begin{align}
-	\sigma_2 & : V_2 \to \values &
-	\sigma_1 \uplus \sigma_2 \uplus \sigma_3 & \vdash R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \hyp{7'} \\
-	&& \sigma_1 \uplus \sigma_3 & \vdash \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \hyp{7"}
-\end{align}
+\begin{gather*}
+	\sigma_2: V_2 \to \values \quad s_2 \in S_2 \\
+	\sigma_1 \uplus \sigma_2 \uplus \sigma_3 \vdash R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \hyp{7'} \\
+	\sigma_1 \uplus \sigma_3 \vdash \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \hyp{7"}
+\end{gather*}
+Hypotheses \hyp{5} and \hyp{6} are considered with the obtained state \(s_2\).
 We can use immediately \hyp{6} with valuation \(\sigma_2 \uplus \sigma_3\) to get \nmm{\nu_2: \biguplus_{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values}.

### 2021-06-06 2021-Refinement/report.tex
Fixed some references, finished proof of transitivity

@@
 However equivalences relations are not always sufficient to perform verification, refinement relations are also used.
-For instance an example of open pNet where equivalence is not sufficient was encountered in an article about algorithms fo weak bisimulation on open automata \cite{wang:hal-03126313}.
+For instance an example of open pNet where equivalence is not sufficient was encountered in an article about algorithms fo weak bisimulation on open automata \cite{wang:03126313}.
 
@@
 
-\section{Proof of equivalent definitions}\label{apx:lemeqd} % TODO: disjunction branch, say where we get the value
+\section{Proof of equivalent definitions}\label{apx:lemeqd}
 
@@
 	\[ \exists t_2 \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \vdash \fguard{t_2} \hyp{2} \]
-	And get immediately the values \(t_2\), \(\nu\) and the hypothesis:
+	And get immediately a transition \(t_2 \in \fOT{s_2}\), a valuation \(\nu: \fvars{t_2} \to \values\) and the hypothesis:
 	\[ \sigma \uplus \nu \vdash \fguard{t_2} \hyp{2'} \]
@@
 	The left side of the implication is proved using \hyp{1} and \hyp{2'} for the branch \(t_2\) of the disjunction.
-	We are now allowed to decompose the right side to get \(t_1\) such that:
+	The right side is a disjunction so there is a \(t_1 \in \fOT{s_1}\) such that:
 	\[ \sigma \uplus \nu \uplus \mu \vdash \fguard{t_1} \hyp{3'} \]
-	At this point we have a certain \(t_1\) and \(t_2\) so we may be tempted to use them to prove the goal:
+	At this point we have a pair \(\mpar{t_1, t_2}\) so we may be tempted to use it to prove the goal:
 	\begin{multline}
@@
 	\[ \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{2} \]
-	We can admit the left part of the implication in which we decompose the big disjunction to get \(t_2 \in \fOT{s_2}\) and:\\
+	We can admit the left part of the implication in which the big disjunction gives us a \(t_2 \in \fOT{s_2}\) and:
 	\begin{gather}
@@
 	\[ \exists t_p \in \fOT{s_p}, \exists \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \vdash \fguard{t_p} \hyp{2} \]
-	We get immediately the values \(t_p\), \(\nu\) and the hypothesis:
+	We get immediately a transition \(t_p \in \fOT{s_p}\), a valuation \(\nu: \fvars{t_p} \to \values\) and the hypothesis:
 	\[ \sigma \uplus \nu \vdash \fguard{t_p} \hyp{2'} \]
@@
 	The left side of the implication is proved using \hyp{1} and \hyp{2'} for the branch \(t_p\) of the disjunction.
-	We are now allowed to decompose the right side to get \(t\) such that:
+	The right side is a big disjunction that gives us \(t \in \fOT{s}\) such that:
 	\[ \sigma \uplus \nu \uplus \mu \vdash \fguard{t} \hyp{3'} \]
@@
 	\[ \sigma \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \goal{1} \]
-	We can admit the left part of the implication in which we decompose the big disjunction to get \(t_p\) and:\\
-	\begin{minipage}{0.5\textwidth}\[ \sigma \vdash \reach{A}\mpar{s} \hyp{4} \]\end{minipage}
-	\begin{minipage}{0.5\textwidth}\[ \sigma \vdash \fguard{t_p} \hyp{5} \]\end{minipage}
+	We can admit the left part of the implication in which the big disjunction gives us \(t_p \in \fOT{s_p}\) and:\\
+	\begin{gather}
+		\sigma \vdash \reach{A}\mpar{s} \hyp{4} \\
+		\sigma \vdash \fguard{t_p} \hyp{5}
+	\end{gather}
 	We are left to prove:
@@
 \defitem By transitivity of \(\triangle\), \(J_1 \triangle J_3\)
-\defitem We prove that initial configurations are related using \(\sigma_{02}\) as the values of the variables in \(V_2\), and \(s_{02}\) as the branch of the disjunction.
+\defitem We prove that initial configurations are related using \(\sigma_{02}\) as the values of the variables in \(V_2\), and \(s_{02}\) to choose the branch of the disjunction.
 \begin{gather*}
@@
 		\mpar{t_{s2x} \defobject \OT{s_2}{s'_{s2x}}{\alpha_{s2x}}{\beta_{s2xj}^{j \in J'_{s2x}}}{g_{s2x}}{\psi_{s2x}} \in \fOT{s_2}}^{x \in X_{s2}} \\
-	\mpar{\forall x \in X, J'_{s2x} \cap J_1 = J'_1 \cap J_2} \hyp{0'} \\
+		\forall x \in X, J'_{s2x} \cap J_1 = J'_1 \cap J_2 \hyp{0'} \\
 		V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R_{12}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X_{s2}} \mpar{\everymath{\displaystyle}\begin{array}{l}
@@
 		\mpar{t_{3z} \defobject \OTx{3}{z}{3z}{3z} \in \fOT{s_3}}^{z \in Z_{s2x}} \\
-	\mpar{\forall z \in Z_{s2x}, J'_{3z} \cap J_2 = J'_{s2x} \cap J_3} \hyp{1x} \\
+		\forall z \in Z_{s2x}, J'_{3z} \cap J_2 = J'_{s2x} \cap J_3 \hyp{1x} \\
 		V_2 \uplus V_3 \uplus \fvars{t_{s2x}} \vdash R_{23}\mpar{s_2, s_3} \wedge g_{s2x} \Rightarrow \operatorname*{\bigsymb{\bigvee}}_\subbox{z \in Z_{s2x}} \mpar{\!\everymath{\displaystyle}\begin{array}{l}
@@
 	\end{gather}
-\item[\goal{2}:] Case on \(\triangle\):
+\item[\goal{2}:] By case on \(\triangle\):
 	\begin{itemize}
@@
 		J'_{3z} \cap J_1 & \subseteq J'_{3z} \cap J_2 & \text{by } & J_1 \subseteq J_2 \\
-		& \subseteq J'_{2x} \cap J_3 & \text{by } & \text{\hyp{1x}} \\
+			& \subseteq J'_{2x} \cap J_3 & \text{by } & \text{\hyp{1x}} \hyp{2} \\
 			& \subseteq J'_{2x} \cap J_3 \cap J_1 & \text{by } & J'_{3z} \cap J_1 \subseteq J_1 \\
 			& \subseteq J'_{2x} \cap J_1 && \\
-		& \subseteq J'_1 \cap J_2 & \text{by } & \text{\hyp{0'}} \\
+			& \subseteq J'_1 \cap J_2 & \text{by } & \text{\hyp{0'}} \hyp{2'} \\
 			& \subseteq J'_1 \cap J_3 & \text{by } & J_2 \subseteq J_3
@@
 		J'_{3z} \cap J_1 & = J'_{3z} = J'_{3z} \cap J_2 & \text{by } & J_1 \supseteq J_2 \supseteq J_3 \supseteq J'_{3z} \\
-		& = J'_{2x} \cap J_3 & \text{by } & \text{\hyp{1x}} \\
+			& = J'_{2x} \cap J_3 & \text{by } & \text{\hyp{1x}} \hyp{3} \\
 			& \subseteq J'_{2x} \cap J_1 & \text{by } & J_1 \supseteq J_3 \\
-		& \subseteq J'_1 \cap J_2 & \text{by } & \text{\hyp{0'}} \\
+			& \subseteq J'_1 \cap J_2 & \text{by } & \text{\hyp{0'}} \hyp{3'} \\
 			& \subseteq J'_1 \cap J_2 \cap J_3 & \text{by } & J'_{3z} \subseteq J_3 \\
@@
 	We use dummy values for variables in \nmm{\biguplus_\subbox{z \in Z} \fvars{t_{3z}}} to get the left side of this implication as an hypothesis (independant from these values):
-\[ \sigma_1 \uplus \sigma_3 \vdash R_{13}\mpar{s_1, s_3} \wedge g_1 \hyp{2} \]
+	\[ \sigma_1 \uplus \sigma_3 \vdash R_{13}\mpar{s_1, s_3} \wedge g_1 \hyp{4} \]
 	Hypothesis that we immediately break down into
@@
 		\sigma_2: V_2 \to \values \quad s_2 \in S_2 \\
-	\sigma_1 \uplus \sigma_2 \uplus \sigma_3 \vdash R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \hyp{2'} \\
-	\sigma_1 \vdash g_1 \hyp{2"}
+		\sigma_1 \uplus \sigma_2 \uplus \sigma_3 \vdash R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \hyp{4'} \\
+		\sigma_1 \vdash g_1 \hyp{4"}
 	\end{gather*}
 	We can use immediately \hyp{0"} with valuation \(\sigma_1 \uplus \sigma_2\) to get \nmm{\nu_2: \biguplus_{x \in X} \fvars{t_{2x}} \to \values}.
-The left side of the implication is proved with the right side of \hyp{2'} and \hyp{2"}, so we get \(x \in X_{s2}\) and the hypotheses
+	The left side of the implication is proved with the right side of \hyp{4'} and \hyp{4"}, so we get \(x \in X_{s2}\) and the hypotheses
 	\begin{align}
-	\sigma_1 \uplus \sigma_2 \uplus \nu_2 & \vdash \alpha_1 = \alpha_{s2x} \hyp{3a} \\
-	\sigma_1 \uplus \sigma_2 \uplus \nu_2 & \vdash \bigwedge_\subbox{j \in J'_1 \cap J'_{s2x}} \beta_{1j} = \beta_{s2xj} \hyp{3b} \\
-	\sigma_2 \uplus \nu_2 & \vdash g_{s2x} \hyp{3c} \\
-	\sigma_1 \uplus \sigma_2 \uplus \nu_2 & \vdash R\mpar{s'_1, s'_{s2x}}\psubst{\psi_1 \uplus \psi_{s2x}} \hyp{3d}
+		\sigma_1 \uplus \sigma_2 \uplus \nu_2 & \vdash \alpha_1 = \alpha_{s2x} \hyp{5a} \\
+		\sigma_1 \uplus \sigma_2 \uplus \nu_2 & \vdash \bigwedge_\subbox{j \in J'_1 \cap J_{s2x}} \beta_{1j} = \beta_{s2xj} \hyp{5b} \\
+		\sigma_2 \uplus \nu_2 & \vdash g_{s2x} \hyp{5c} \\
+		\sigma_1 \uplus \sigma_2 \uplus \nu_2 & \vdash R\mpar{s'_1, s'_{s2x}}\psubst{\psi_1 \uplus \psi_{s2x}} \hyp{5d}
 	\end{align}
 	We can now use \hyp{1x'} with valuation \(\sigma_2 \uplus \nu_2 \uplus \sigma_3\) to get \nmm{\nu_3: \biguplus_{Z \in Z_{s2x}} \fvars{t_{3z}} \to \values}.
-The left side of the implication is proved with the left side of \hyp{2'} and \hyp{2"}, so we get \(z \in Z_{s2x}\) and the hypotheses
+	The left side of the implication is proved with the left side of \hyp{4'} and \hyp{4"}, so we get \(z \in Z_{s2x}\) and the hypotheses
 	\begin{align}
-	\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3 & \vdash \alpha_{s2x} = \alpha_{3z} \hyp{4a} \\
-	\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3 & \vdash \bigwedge_\subbox{j \in J'_{s2x} \cap J'_{3z}} \beta_{s2xj} = \beta_{3zj} \hyp{4b} \\
-	\sigma_3 \uplus \nu_3 & \vdash g_{3z} \hyp{4c} \\
-	\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3 & \vdash R\mpar{s'_{s2x}, s'_{3z}}\psubst{\psi_{s2x} \uplus \psi_{3z}} \hyp{4d}
+		\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3 & \vdash \alpha_{s2x} = \alpha_{3z} \hyp{6a} \\
+		\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3 & \vdash \bigwedge_\subbox{j \in J'_{s2x} \cap J_{3z}} \beta_{s2xj} = \beta_{3zj} \hyp{6b} \\
+		\sigma_3 \uplus \nu_3 & \vdash g_{3z} \hyp{6c} \\
+		\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3 & \vdash R\mpar{s'_{s2x}, s'_{3z}}\psubst{\psi_{s2x} \uplus \psi_{3z}} \hyp{6d}
 	\end{align}
@@
 	\end{align}
-\goal{3a} is proved by transitivity using \hyp{3a} and \hyp{4a}.
-\goal{3b} depends on \(\triangle\).
-If \(\triangle\) is \(\subseteq\) % TODO
-If \(\triangle\) is \(\supseteq\) % TODO
-\goal{3c} is exactly \hyp{4c}.
-We prove \goal{3d} with valuation \(\mpar{\sigma_2 \uplus \nu_2}\psubst{\psi_{s2x}}\) for the branch \(s_2\):
+	\goal{3a} is proved by transitivity using \hyp{5a} and \hyp{5a}.
+	\goal{3b} is proved using \hyp{5b} and \hyp{6b}, but depending on \(\triangle\) the equality are obtained for the interesting values \(j\) using either \hyp{2} and \hyp{2'} or \hyp{3} and \hyp{3'}.
+	\goal{3c} is exactly \hyp{6c}.
+	We prove \goal{3d} with valuation \(\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}\) for the branch \(s_2\) using \hyp{5d} and \hyp{6d}:
 	\begin{multline*}
-	\mpar{R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}}\psubst{\psi_1 \uplus \psi_{3z}}\psubst{\mpar{\sigma_2 \uplus \nu_2}\psubst{\psi_{s2x}}} \\
-	= R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} % TODO
+		\mpar{R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}}\psubst{\psi_1 \uplus \psi_{3z}}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_1 \uplus \sigma_3 \uplus \nu_3} \\
+		= R_{12}\mpar{s_1, s_2}\psubst{\psi_1}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_1} \wedge R_{23}\mpar{s_2, s_3}\psubst{\psi_{3z}}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_3 \uplus \nu_3} \\
+		= R_{12}\mpar{s_1, s_2}\psubst{\psi_1 \uplus \psi_{s2x}}\psubst{\sigma_2 \uplus \nu_2 \uplus \sigma_1} \wedge R_{23}\mpar{s_2, s_3}\psubst{\psi_{3z} \uplus \psi_{s2x}}\psubst{\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3}
 	\end{multline*}
 \item[\goal{1}:] Let \(\sigma_1: V_1 \to \values\) and \nmm{\sigma_3: V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \to \values}.
-We have the hypotheses on \(R_{12}\) and \(R_{23}\) for a specific \(s_2\), then the current goal:
+	We have the hypotheses on \(R_{12}\) and \(R_{23}\) for the states \(s_1\) and \(s_3\), then the current goal:
 	\begin{gather}
-	V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{5} \\
-	V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash R_{23}\mpar{s_2, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{6} \\
+		\forall s_2 \in \fOT{s_2}, V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{7} \\
+		\forall s_2 \in \fOT{s_2}, V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash R_{23}\mpar{s_2, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{8} \\
 		\sigma_1 \uplus \sigma_3 \vdash R_{13}\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{1'}
@@
 	We use dummy values for variables in \nmm{\biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1}} to get the left side of this implication as an hypothesis (independant from these values):
-\[ \sigma_1 \uplus \sigma_3 \vdash R_{13}\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \hyp{7} \]
+	\[ \sigma_1 \uplus \sigma_3 \vdash R_{13}\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \hyp{9} \]
 	Hypothesis that we immediately break down into:
@@
 		\sigma_2: V_2 \to \values \quad s_2 \in S_2 \\
-	\sigma_1 \uplus \sigma_2 \uplus \sigma_3 \vdash R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \hyp{7'} \\
-	\sigma_1 \uplus \sigma_3 \vdash \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \hyp{7"}
+		\sigma_1 \uplus \sigma_2 \uplus \sigma_3 \vdash R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \hyp{9'} \\
+		\sigma_1 \uplus \sigma_3 \vdash \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \hyp{9"}
 	\end{gather*}
-Hypotheses \hyp{5} and \hyp{6} are considered with the obtained state \(s_2\).
-We can use immediately \hyp{6} with valuation \(\sigma_2 \uplus \sigma_3\) to get \nmm{\nu_2: \biguplus_{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values}.
-The left side of the implication is proved with the right side of \hyp{7'} and \hyp{7"}, so we get
-\[ \sigma_3 \uplus \nu_2 \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{6'} \]
-We can now use \hyp{5} with valuation \(\sigma_1 \uplus \sigma_2 \uplus \nu_2\) to get \nmm{\nu_1: \biguplus_{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
-The left side of the implication is proved with the left side of \hyp{7'} and \hyp{6'}, so we get
-\[ \sigma_1 \uplus \nu_1 \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{5'} \]
-Finally we can prove \goal{1'} with valuation \(\nu_1\) for the implicit \(\exists\) by admitting the left side of the implication and using \hyp{5'} for the right side.
+	We can use immediately \hyp{8} with state \(s_2\) and valuation \(\sigma_2 \uplus \sigma_3\) to get \nmm{\nu_2: \biguplus_{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values}.
+	The left side of the implication is proved with the right side of \hyp{9'} and \hyp{9"}, so we get
+	\[ \sigma_3 \uplus \nu_2 \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{8'} \]
+	We can now use \hyp{7} with state \(s_2\) and valuation \(\sigma_1 \uplus \sigma_2 \uplus \nu_2\) to get \nmm{\nu_1: \biguplus_{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
+	The left side of the implication is proved with the left side of \hyp{9'} and \hyp{8'}, so we get
+	\[ \sigma_1 \uplus \nu_1 \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{7'} \]
+	Finally we can prove \goal{1'} with valuation \(\nu_1\) for the implicit \(\exists\) by admitting the left side of the implication and using \hyp{7'} for the right side.
 \end{proof}

### 2021-06-08 2021-Refinement/report.tex
Sync

@@
 However we cannot talk about states in formulas.
-The solution is to expand the existential quantifier as we did in deadlock prevention, which is possible because states are finite.
+The solution is to expand the existential quantifier on states as we did in deadlock prevention, which is possible because states are finite.
 \nmm{R_{13} \defobject \mpar{s_1, s_3} \mapsto \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}} is a witness of the transitivity, proof is given in appendix \ref{apx:trans}.
@@
 \begin{proof}
-% TODO: assume a <= b & a[c] -> b[c] + proof
+	For three open automata \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\), let \(k \in J_1\), \(A_{13} \defobject A_1\subst{A_3}{k}\) and \(A_{23} \defobject A_2\subst{A_3}{k}\) with \(A_{13} = \OAg[13]\) and \(A_{23} = \OAg[23]\).
+	Let \(R_{12}\) be a hole-equal simulation of \(A_1\) by \(A_2\) and \(\reach{A_{13}}\) be a witness that \(A_{13}\) is non-locking.
+	The idea for the relation on configurations is that \(A_2\) simulates \(A_1\) while \(A_3\) does the same things in both compositions.
+	We pose
+	\[ R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \bigwedge_{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \]
+	Where \(y_{3x}\) is the renaming of \(y_3\) from \(A_3\) in \(A_{x3}\).
+	We want to prove that \(R\) is a hole-equal simulation of \(A_{12}\) by \(A_{23}\):
+	\begin{gather}
+		J_1 \cup J_3 \setminus \mbrc{k} = J_2 \cup J_3 \setminus \mbrc{k} \goal{1a} \\
+		\sigma_{013} \uplus \sigma_{023} \vdash R\mpar{s_{013}, s_{023}} \goal{1b}
+	\end{gather}\vspace{-1cm}
+	\begin{multline}
+		\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}, \\
+		\mpar{\everymath{\displaystyle}\begin{array}{l}
+			\bigsymb{\forall} t_{13} \defobject \OTx{13}{}{13}{13} \in \fOT{s_{13}}, \bigsymb{\exists} \mpar{t_{23x} \defobject \OTx{23}{x}{23x}{23x} \in \fOT{s_{23}}}^{x \in X}, \\
+			\quad \mpar{\forall x \in X, J'_{23x} \cap J_{13} = J'_{13} \cap J_{23}} \\[-10pt]
+			\nwedge V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{232}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+				\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \\[12pt]
+				\nwedge g_{23x} \wedge R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
+			\end{array}}
+		\end{array}} \\
+		\wedge V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash R\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \goal{1c}
+	\end{multline}
+	\goal{1a} is proved by rewriting using the hypothesis \(J_1 = J_2\) from the simulation.
+	For \goal{1b} we use the fact that \(R_{12}\) relates inital configurations:
+	\begin{align*}
+		\sigma_{013} \uplus \sigma_{023} \vdash R\mpar{s_{013}, s_{023}} \iff & R\mpar{\mpar{s_{01}, s_{031}}, \mpar{s_{02}, s_{031}}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{031} \uplus \sigma_{032}} \\
+		\iff & R_{12}\mpar{s_{01}, s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02}} \wedge \mpar{\bigwedge_{v_3 \in V_3} v_{31} = v_{32}}\psubst{\sigma_{031} \uplus \sigma_{032}} \\
+		\iff & R_{12}\mpar{s_{01}, s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02}} \wedge \bigwedge_{v_3 \in V_3} \sigma_{031}\mpar{v_{31}} = \sigma_{032}\mpar{v_{32}} \\
+		\iff & R_{12}\mpar{s_{01}, s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02}} \wedge \top \\
+		\iff & \sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}
+	\end{align*}
+	Let \(s_{13} \defobject \mpar{s_1, s_{31}} \in S_{13}\) and \(s_{23} \defobject \mpar{s_2, s_{32}} \in S_{23}\).
+	The goals left to prove are
+	\begin{align*}
+		& \bigsymb{\forall} t_{13} \defobject \OTx{13}{}{13}{13} \in \fOT{s_{13}}, \bigsymb{\exists} \mpar{t_{23x} \defobject \OTx{23}{x}{23x}{23x} \in \fOT{s_{23}}}^{x \in X}, \\
+		& \quad \mpar{\forall x \in X, J'_{23x} \cap J_{13} = J'_{13} \cap J_{23}} \\[-10pt]
+		& \nwedge V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{232}} \wedge g_{13} \Rightarrow \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\!\!\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \\[12pt]
+			\nwedge g_{23x} \wedge R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
+		\end{array}\!\!} \goal{2}
+	\end{align*}
+	\[ V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash R\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \goal{3} \]
+\item[\goal{2}:] % TODO: introduce t_... then hyps
+\item[\goal{3}:] % TODO: introduce hyps
 \end{proof}
@@
 \begin{proof}
-% TODO
+	Let \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\) be open automata.
+	Let \(k \in J_1\) and \(A \defobject A_1\subst{A_2}{k}\).
+	Let \(\reach{A}\) be a witness that \(A\) is non-locking.
+	The idea for the relation on configurations is that the copy of \(A_1\) in \(A\) do the same things as if we were to try proving reflexivity.
+	We pose
+	\[ R \defobject \mpar{\mpar{s_1, s_2}, s'_1} \mapsto \choice{\bigwedge_{v \in V_1} v = v' & \text{if } s_1 = s'_1 \\ \bot & \text{otherwise}} \]
+	% TODO: proove A \leq A_1
 \end{proof}
@@
 % Yet having untracked holes is interesting because we can be a refinement of several OA, each on different holes.
-
-\section{Flat model}
-% Goal: some interfaces refine in one way while other refine in the other way and others are equivalent and some are untracked.
 
@@
 	\[ \sigma \uplus \nu \vdash \fguard{t_2} \hyp{2'} \]
-	\(R\) satisfies \eqref{eq:drWD} with the current value of \(\mpar{s_1, s_2}\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \(\biguplus_{t_2 \in \fOT{s_2}} \fvars{t_2}\) so we have:
+	\(R\) satisfies \eqref{eq:drWD} with the current value of \(\mpar{s_1, s_2}\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \nmm{\biguplus_{t_2 \in \fOT{s_2}} \fvars{t_2}} so we have:
 	\[ \sigma \uplus \nu \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{3} \]
@@
 	However we cannot yet prove it because we don't know whether \(t_2\) and \(t_1\) match.
-	In order to get a \(t_2\) matching \(t_1\) we will use the fact that \(R\) is a simulation.
+	In order to get a \(t_2\) matching \(t_1\) we will use the fact that \(R\) is a pre-simulation.
 	\begin{multline}
@@
 \defitem We prove that initial configurations are related using \(\sigma_{02}\) as the values of the variables in \(V_2\), and \(s_{02}\) to choose the branch of the disjunction.
-\begin{gather*}
-	\sigma_{01} \uplus \sigma_{03} \vdash R_{13}\mpar{s_{01}, s_{03}} \\
-	\equiv \\
-	\sigma_{01} \uplus \sigma_{03} \vdash \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_{01}, s_2} \wedge R_{23}\mpar{s_2, s_{03}} \\
-	\Uparrow \\
-	\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03} \vdash R_{12}\mpar{s_{01}, s_{02}} \wedge R_{23}\mpar{s_{02}, s_{03}} \\
-	\Uparrow \\
-	\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar{\sigma_{02} \uplus \sigma_{03} \vdash R_{23}\mpar{s_{02}, s_{03}}}
-\end{gather*}
+\begin{align*}
+	\sigma_{01} \uplus \sigma_{03} \vdash R_{13}\mpar{s_{01}, s_{03}} \iff & \sigma_{01} \uplus \sigma_{03} \vdash \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_{01}, s_2} \wedge R_{23}\mpar{s_2, s_{03}} \\
+	\impliedby & \sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03} \vdash R_{12}\mpar{s_{01}, s_{02}} \wedge R_{23}\mpar{s_{02}, s_{03}} \\
+	\impliedby & \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar{\sigma_{02} \uplus \sigma_{03} \vdash R_{23}\mpar{s_{02}, s_{03}}}
+\end{align*}
 \defitem Let \(\mpar{s_1, s_3} \in S_1 \times S_3\), we want to prove both
-	\begin{multline}
-		\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{3x} \defobject \OTx{3}{x}{3x}{3x} \in \fOT{s_3}}^{x \in X}, \\
-		\mpar{\forall x \in X, J'_{3x} \cap J_1 = J'_1 \cap J_3} \\
-		\wedge V_1 \uplus V_3 \uplus \fvars{t_1} \vdash R_{13}\mpar{s_1, s_3} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+	\begin{align*}
+		& \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{3x} \defobject \OTx{3}{x}{3x}{3x} \in \fOT{s_3}}^{x \in X}, \\
+		& \mpar{\forall x \in X, J'_{3x} \cap J_1 = J'_1 \cap J_3} \\[-10pt]
+		& \wedge V_1 \uplus V_3 \uplus \fvars{t_1} \vdash R_{13}\mpar{s_1, s_3} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
 			\alpha_1 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x} \cap J_1} \beta_{1j} = \beta_{3xj} \\[12pt]
@@
 		\end{array}} \goal{0}
-	\end{multline}
+	\end{align*}
 	\[ V_1 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash R_{13}\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{1} \]
@@
 	We prove \goal{3d} with valuation \(\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}\) for the branch \(s_2\) using \hyp{5d} and \hyp{6d}:
-	\begin{multline*}
-		\mpar{R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}}\psubst{\psi_1 \uplus \psi_{3z}}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_1 \uplus \sigma_3 \uplus \nu_3} \\
-		= R_{12}\mpar{s_1, s_2}\psubst{\psi_1}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_1} \wedge R_{23}\mpar{s_2, s_3}\psubst{\psi_{3z}}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_3 \uplus \nu_3} \\
-		= R_{12}\mpar{s_1, s_2}\psubst{\psi_1 \uplus \psi_{s2x}}\psubst{\sigma_2 \uplus \nu_2 \uplus \sigma_1} \wedge R_{23}\mpar{s_2, s_3}\psubst{\psi_{3z} \uplus \psi_{s2x}}\psubst{\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3}
-	\end{multline*}
+	\begin{align*}
+		& \sigma_1 \uplus \sigma_3 \uplus \nu_3 \vdash R_{13}\mpar{s'_1, s'_{3z}}\psubst{\psi_1 \uplus \psi_{3z}} \\
+		\iff & \mpar{R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}}\psubst{\psi_1 \uplus \psi_{3z}}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_1 \uplus \sigma_3 \uplus \nu_3} \\
+		\iff & R_{12}\mpar{s_1, s_2}\psubst{\psi_1}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_1} \wedge R_{23}\mpar{s_2, s_3}\psubst{\psi_{3z}}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_3 \uplus \nu_3} \\
+		\iff & R_{12}\mpar{s_1, s_2}\psubst{\psi_1 \uplus \psi_{s2x}}\psubst{\sigma_2 \uplus \nu_2 \uplus \sigma_1} \wedge R_{23}\mpar{s_2, s_3}\psubst{\psi_{3z} \uplus \psi_{s2x}}\psubst{\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3} \\
+		\iff & \mpar{\sigma_2 \uplus \nu_2 \uplus \sigma_1 \vdash R_{12}\mpar{s_1, s_2}\psubst{\psi_1 \uplus \psi_{s2x}}} \wedge \mpar{\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3 \vdash R_{23}\mpar{s_2, s_3}\psubst{\psi_{3z} \uplus \psi_{s2x}}}
+	\end{align*}
 \item[\goal{1}:] Let \(\sigma_1: V_1 \to \values\) and \nmm{\sigma_3: V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \to \values}.

### 2021-06-09 2021-Refinement/report.tex
Proof of th3

@@
 An example of composition can be found in Appendix \ref{apx:composition}.
-\begin{prop}[Parallel composition]
+\begin{prop}[Simultaneous composition]
 Let \(A_1\), \(A_2\), \(A_3\) be three open automata with respectively \(J_1\), \(J_2\) and \(J_3\) as hole names.
@@
 \defitem Inital state is reachable: \(\sigma_0 \vdash \reach{A}\mpar{s_0}\)
-\defitem Reachability is preserved across transitions: \nmm{\bigsymb{\forall} t \defobject \OTg \in T, \forall \nu: \fvars{t} \to \values, \nu \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}}
+\defitem Reachability is preserved across transitions: \nmm{\bigsymb{\forall} t \defobject \OTg \in T, \fvars{t} \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}}
 \end{defi}
@@
 A relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if it is a pre-simulation and it satisfies the following:
-\begin{multline*}
-	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values, \\
-	\sigma \vdash \mpar{R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
-\end{multline*}
+\[ \forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \]
 \end{defi}
@@
 The composition \(A \defobject A_p\subst{A_c}{j}\) is a non-locking composition if:
-\[ \forall s \defobject \mpar{s_p, s_c} \in S, \forall \sigma: V \uplus \biguplus_\subbox{t_p \in \fOT{s_p}} \fvars{t_p} \to \values, \sigma \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
+\[ \forall s \defobject \mpar{s_p, s_c} \in S, V \uplus \biguplus_\subbox{t_p \in \fOT{s_p}} \fvars{t_p} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
 \end{defi}
@@
 \end{multline}
-\[ \implies \]
+\[ \bigsymb{\implies} \]\vspace{-1cm}
 \begin{multline}
@@
 	We want to prove that \(R\) is a hole-equal simulation of \(A_{12}\) by \(A_{23}\):
-	\begin{gather}
-		J_1 \cup J_3 \setminus \mbrc{k} = J_2 \cup J_3 \setminus \mbrc{k} \goal{1a} \\
-		\sigma_{013} \uplus \sigma_{023} \vdash R\mpar{s_{013}, s_{023}} \goal{1b}
-	\end{gather}\vspace{-1cm}
-	\begin{multline}
-		\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}, \\
-		\mpar{\everymath{\displaystyle}\begin{array}{l}
-			\bigsymb{\forall} t_{13} \defobject \OTx{13}{}{13}{13} \in \fOT{s_{13}}, \bigsymb{\exists} \mpar{t_{23x} \defobject \OTx{23}{x}{23x}{23x} \in \fOT{s_{23}}}^{x \in X}, \\
-			\quad \mpar{\forall x \in X, J'_{23x} \cap J_{13} = J'_{13} \cap J_{23}} \\[-10pt]
-			\nwedge V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{232}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-				\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \\[12pt]
-				\nwedge g_{23x} \wedge R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
-			\end{array}}
-		\end{array}} \\
-		\wedge V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash R\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \goal{1c}
-	\end{multline}
-	\goal{1a} is proved by rewriting using the hypothesis \(J_1 = J_2\) from the simulation.
-	For \goal{1b} we use the fact that \(R_{12}\) relates inital configurations:
+\defitem \(J_{13} = J_3 \cup J_1 \setminus \mbrc{k} = J_3 \cup J_2 \setminus \mbrc{k} = J_{23}\) by \(J_1 = J_2\).
+\defitem For \(\sigma_{013} \uplus \sigma_{023} \vdash R\mpar{s_{013}, s_{023}}\) we use the fact that \(R_{12}\) relates inital configurations:
 	\begin{align*}
@@
 	\end{align*}
-	Let \(s_{13} \defobject \mpar{s_1, s_{31}} \in S_{13}\) and \(s_{23} \defobject \mpar{s_2, s_{32}} \in S_{23}\).
-	The goals left to prove are
+\defitem Let \(s_{13} \defobject \mpar{s_1, s_{31}} \in S_{13}\) and \(s_{23} \defobject \mpar{s_2, s_{32}} \in S_{23}\).
+	We want to prove both
 	\begin{align*}
@@
 		& \quad \mpar{\forall x \in X, J'_{23x} \cap J_{13} = J'_{13} \cap J_{23}} \\[-10pt]
-		& \nwedge V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{232}} \wedge g_{13} \Rightarrow \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\!\!\everymath{\displaystyle}\begin{array}{l}
+		& \nwedge V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \Rightarrow \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\!\!\everymath{\displaystyle}\begin{array}{l}
 			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \\[12pt]
 			\nwedge g_{23x} \wedge R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
-		\end{array}\!\!} \goal{2}
-	\end{align*}
-	\[ V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash R\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \goal{3} \]
-\item[\goal{2}:] % TODO: introduce t_... then hyps
-\item[\goal{3}:] % TODO: introduce hyps
+		\end{array}\!\!} \goal{1}
+	\end{align*}
+	\[ V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash R\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \goal{2} \]
+	Let \nmm{t_{13} \defobject \OTx{13}{}{13}{13} \in \fOT{s_{13}}}, we use the fact that \(R_{12}\) is a simulation from the states \(\mpar{s_1, s_2}\) to get the hypothesis:
+	\begin{align*}
+		& \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
+		& \quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
+		& \nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
+			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}} \hyp{5}
+	\end{align*}
+	Transition \(t_{13}\) is obtained in \(A_{13}\) by composition of two transitions \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}} and \nmm{t_3 \defobject \OTx{3}{}{3}{3} \in \fOT{s_3}} if \(k \in J'_1\) or by a the first transition and a fixed state \(s_3 \in S_3\) if \(k \notin J'_1\).
+	We use \hyp{5} with the transition \(t_1\) to get
+	\begin{gather*}
+		\mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X} \\
+		\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2 \hyp{5'} \\
+		V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
+			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}} \hyp{5"}
+	\end{gather*}
+	To build the family of transitions we need to know if \(k \in J'_{2x}\) for a every \(x \in X\):
+	\begin{align*}
+		J'_1 & = J'_1 \cap J_1 \\
+		& = J'_1 \cap J_2 & \text{by } J_1 = J_2 \\
+		& = J'_{2x} \cap J_1 & \text{by \hyp{5'}} \\
+		& = J'_{2x} \cap J_2 & \text{by } J_1 = J_2 \\
+		& = J'_{2x} \hyp{6}
+	\end{align*}
+	Using \hyp{6} we can build the familly of transition generated by the family \(t_{2x}^{x \in X}\):
+	\[ t_{23x}^{x \in X} \defobject x \mapsto \choice{
+		\OT{\mpar{s_2, s_3}}{\mpar{s'_{2x}, s'_3}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x} \setminus \mbrc{k}} \uplus \beta_{3j}^{j \in J'_3}}{g_{2x} \wedge g_3 \wedge \alpha_3 = \beta_{2xk}}{\psi_{2x} \uplus \psi_3} & \text{if } k \in J'_{2x} \\
+		\OT{\mpar{s_2, s_3}}{\mpar{s'_{2x}, s_3}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_2}}{g_2}{\psi_2} & \text{if } k \notin J'_{2x}
+	} \]
+	We will prove \goal{1} for the family \(t_{23x}^{x \in X}\), the new goals are
+	\begin{gather}
+		\forall x \in X, J'_{23x} \cap J_{13} = J'_{13} \cap J_{23} \goal{1'} \\
+		V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \\[12pt]
+			\nwedge g_{23x} \wedge R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
+		\end{array}} \goal{3}
+	\end{gather}
+\item[\goal{1'}:] Let \(x \in X\), by case on \(k \in J'_1\):
+	\begin{align*}
+		\text{If } k \in J'_1: && J'_{23x} \cap J_{13} & = \mpar{J'_3 \cup J'_{2x} \setminus \mbrc{k}} \cap \mpar{J_3 \cup J_1 \setminus \mbrc{k}} \\
+		&&& = \mpar{J'_3 \cap J_3} \cup \mpar{J'_{2x} \cap J_1} \setminus \mbrc{k} \\
+		&&& = \mpar{J'_3 \cap J_3} \cup \mpar{J'_1 \cap J_2} \setminus \mbrc{k} & \text{by \hyp{5'}} \\
+		&&& = \mpar{J'_3 \cup J'_1 \setminus \mbrc{k}} \cap \mpar{J_3 \cup J_2 \setminus \mbrc{k}} \\
+		&&& = J'_{13} \cap J_{23} \\
+		\text{If } k \notin J'_1: && J'_{23x} \cap J_{13} & = \mpar{J'_{2x} \setminus \mbrc{k}} \cap \mpar{J_1 \setminus \mbrc{k}} \\
+		&&& = J'_{2x} \cap J_1 & \text{by } k \notin J'_1 = J'_{2x} \text{ \hyp{6}} \\
+		&&& = J'_1 \cap J_2 & \text{by \hyp{5'}} \\
+		&&& = \mpar{J'_1 \setminus \mbrc{k}} \cap \mpar{J_2 \setminus \mbrc{k}} & \text{by } k \notin J'_1 \\
+		&&& = J'_{13} \cap J_{23}
+	\end{align*}
+\item[\goal{3}:] Let \(\sigma: V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \to \values\).
+	We use dummy values for the variables in \nmm{\biguplus_{x \in X} \fvars{t_{23x}}} to get the left side of the implication as an hypothesis (independant from these values):
+	\[ \sigma \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \hyp{7} \]
+	Hypothesis immediately breaken down into
+	\begin{gather}
+		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{7a} \\
+		\sigma \vdash \bigwedge_{v_3 \in V_3} v_{31} = v_{32} \hyp{7b} \\
+		\sigma \vdash g_{13} \hyp{7c}
+	\end{gather}
+	We use \hyp{5"} with valuation \(\sigma\) on variables \(V_1 \uplus V_2 \uplus \fvars{t_1}\), which is possible because the composition of transitions doesn't remove any variable (the simplification steps do, they give bisimilar automata).
+	Then we get the values of the implicit \(\exists\) in \nmm{\nu: \biguplus_{x \in X} \fvars{t_{2x}}}.
+	The left side of the implication is proved with \hyp{7a} and \hyp{7c}.
+	So we get a \(x \in X\) such that
+	\begin{gather}
+		\sigma \uplus \nu \vdash \alpha_1 = \alpha_{2x} \hyp{8a} \\
+		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \hyp{8b} \\
+		\sigma \uplus \nu \vdash g_{2x} \hyp{8c} \\
+		\sigma \uplus \nu \vdash R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \hyp{8d}
+	\end{gather}
+	If \(k \in J'_1\), we extend the valuation \(\nu\) to cover the variables of \(t_3\) in \(t_{23x}\) using their value in \(t_{13}\), \(\nu' \defobject \nu \uplus \mset{v_{32} \mapsto \sigma\mpar{v_{31}}}{v \in \fvars{t_3}}\)
+	Otherwise \(\nu' \defobject \nu\).
+	We progress on \goal{3} by giving the valuation \(\sigma \uplus \nu'\) to the implicit \(\exists\), admitting the left side of the implication and choosing to prove the branch \(x\) of the disjunction:
+	\begin{gather}
+		\sigma \uplus \nu' \vdash \alpha_{13} = \alpha_{23x} \goal{3a} \\
+		\sigma \uplus \nu' \vdash \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \goal{3b} \\
+		\sigma \uplus \nu' \vdash g_{23x} \goal{3c} \\
+		\sigma \uplus \nu' \vdash R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}} \goal{3d}
+	\end{gather}
+	Because composition doesn't change the produced actions nor its variables, \goal{3a} is proved by \hyp{8a}.
+	\goal{3b} holds because the valuations for the actions of the holes in \(J_3\) coincide by definition of \(\nu'\) and by \hyp{8b} for the others.
+	For \goal{3c} we have two cases, if \(k \notin J'_1\) then \(g_{23x} \equiv g_{2x}\) and \hyp{8c} is sufficient, if \(k \in J'_1\) then \(g_{23x} \equiv g_{2x} \wedge g_3 \wedge \alpha_3 = \beta_{2xk}\) so we also need \hyp{7c} (\(g_{13} \equiv g_1 \wedge g_3 \wedge \alpha_3 = \beta_{1k}\)) and \hyp{8b} for the value \(k\) (\(\beta_{1k} = \beta_{2xk}\)).
+	\goal{3d} is proved using \hyp{8d} and \hyp{7b}:
+	\begin{align*}
+		& \sigma \uplus \nu' \vdash R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}} \\
+		\iff & \sigma \uplus \nu' \vdash \mpar{R_{12}\mpar{s'_1, s'_{2x}} \wedge \bigwedge_{v_3 \in V_3} v_{31} = v_{32}}\psubst{\psi_1 \uplus \psi_{31} \uplus \psi_{2x} \uplus \psi_{32}} \\
+		\iff & \sigma \uplus \nu' \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \bigwedge_{v_3 \in V_3} \psi_{31}\mpar{v_{31}} = \psi_{32}\mpar{v_{32}} \\
+		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \bigwedge_{v_3 \in V_3} v_{31} = v_{32}} & \text{by transport on } \psi_3 \circ \sigma
+	\end{align*}
+\item[\goal{2}:] Let \(\sigma_{13}: V_{13} \to \values\) and \nmm{\sigma_{23}: V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \to \values}.
+	\(R_{12}\) is a simulation and \(\reach{A_{13}}\) witnesses the non-locking simulation so we have the hypothesis:
+	\begin{gather}
+		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{10} \\
+		V_1 \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A_{13}}\mpar{s} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{11}
+	\end{gather}
+	% TODO: need vars t13 (vars t1 from simu + vars t3 from t23x)
 \end{proof}
 % Rédiger un paragraphe sur le fait que composer dans l'implem sans deadlock implique qu'il n'y a pas de deadlock quand on compose avec la spec, on voudrais avoirs l'autre sens mais ce n'est pas possible
-\begin{prop}[Composition correctness'] Hole-subset simulation is correct w.r.t.\@ composition. \end{prop}
+\begin{prop}[Composition correctness'] Hole-subset simulation is correct w.r.t.\@ composition with automata without holes. \end{prop}
 \begin{proof}
-	Let \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\) be open automata.
-	Let \(k \in J_1\) and \(A \defobject A_1\subst{A_2}{k}\).
+	Let \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\) be open automata, where \(J_2 = \emptyset\).
+	Let \(k \in J_1\) and \(A \defobject A_1\subst{A_2}{k}\), with \(A = \OAg\).
 	Let \(\reach{A}\) be a witness that \(A\) is non-locking.
-	The idea for the relation on configurations is that the copy of \(A_1\) in \(A\) do the same things as if we were to try proving reflexivity.
+	The idea for the relation on configurations is that the copy of \(A_1\) in \(A\) do the same things as \(A_1\), as if we were trying to prove reflexivity.
 	We pose
-	\[ R \defobject \mpar{\mpar{s_1, s_2}, s'_1} \mapsto \choice{\bigwedge_{v \in V_1} v = v' & \text{if } s_1 = s'_1 \\ \bot & \text{otherwise}} \]
-	% TODO: proove A \leq A_1
+	\[ R \defobject \mpar{\mpar{s_{1'}, s_2}, s_1} \mapsto \choice{\bigwedge_{v_1 \in V_1} v_{1'} = v_1 & \text{if } s_{1'} = s_1 \\ \bot & \text{otherwise}} \]
+	Where \(y_{1'}\) is the renaming of \(y_1\) from \(A_1\) in \(A\).
+	We want to prove that \(R\) is a hole-subset simulation of \(A\) by \(A_1\):
+	\begin{gather}
+		J_2 \cup J_1 \setminus \mbrc{k} \subseteq J_1 \goal{5a} \\
+		\sigma_0 \uplus \sigma_{01} \vdash R\mpar{s_0, s_{01}} \goal{5b}
+	\end{gather}\vspace{-1cm}
+	\begin{multline}
+		\forall \mpar{s, s_1} \in S \times S_1, \\
+		\mpar{\everymath{\displaystyle}\begin{array}{l}
+			\bigsymb{\forall} t \defobject \OTg \in \fOT{s}, \bigsymb{\exists} \mpar{t_{1x} \defobject \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X}, \\
+			\quad \mpar{\forall x \in X, J'_{1x} \cap J = J' \cap J_1} \\[-10pt]
+			\nwedge V \uplus V_1 \uplus \fvars{t} \vdash R\mpar{s, s_1} \wedge g \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+				\alpha = \alpha_{1x} \wedge \bigwedge_\subbox{j \in J'_{1x} \cap J} \beta_j = \beta_{1xj} \\[12pt]
+				\nwedge g_{1x} \wedge R\mpar{s', s'_{1x}}\psubst{\psi \uplus \psi_{1x}}
+			\end{array}}
+		\end{array}} \\
+		\wedge V \uplus V_1 \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash R\mpar{s, s_1} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \goal{5c}
+	\end{multline}
+	\goal{5a} is easy because \(J_2 = \emptyset\).
+	For \goal{5b} we use the fact that we don't constrain the behaviour of \(J_2\):
+	\begin{align*}
+		\sigma_0 \uplus \sigma_{01} \vdash R\mpar{s_0, s_{01}} \iff & \mpar{\bigwedge_{v_1 \in V_1} v_{1'} = v_1}\psubst{\sigma_{01'} \uplus \sigma_{02} \uplus \sigma_{01}} \\
+		\iff & \bigwedge_{v_1 \in V_1} \sigma_{01'}\mpar{v_{1'}} = \sigma_{01}\mpar{v_1} \\
+		\iff & \top
+	\end{align*}
+	Let \(s \defobject \mpar{s_{1'}, s_2} \in S\) and \(s_1 \in S_1\).
+	The goals left to prove are
+	\begin{align*}
+		& \bigsymb{\forall} t \defobject \OTg \in \fOT{s}, \bigsymb{\exists} \mpar{t_{1x} \defobject \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X}, \\
+		& \quad \mpar{\forall x \in X, J'_{1x} \cap J = J' \cap J_1} \\[-10pt]
+		& \nwedge V \uplus V_1 \uplus \fvars{t} \vdash R\mpar{s, s_1} \wedge g \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha = \alpha_{1x} \wedge \bigwedge_\subbox{j \in J'_{1x} \cap J} \beta_j = \beta_{1xj} \\[12pt]
+			\nwedge g_{1x} \wedge R\mpar{s', s'_{1x}}\psubst{\psi \uplus \psi_{1x}}
+		\end{array}} \goal{6}
+	\end{align*}
+	\[ V \uplus V_1 \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash R\mpar{s, s_1} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \goal{7} \]
+\item[\goal{6}:] % TODO: proove each goal
+\item[\goal{7}:] % TODO: proove each goal
 \end{proof}
@@
 One more thing worth noting is that for the left automaton, in the state \(1C\) with a valuation such that \(t < 0\), the counter agent is in a deadlock state.
-We could have defined the non-locking composition so that this is considered as an intended deadlock, making the requirement symetric.
-However the the semantics of composition in a hole is assymetric and the considered specification -as in the deadlock prevention- is the parent automaton.
-A symetric version of composition on a flat model of open automata is presented in Section ???\marginpar{TODO LATER}.
+We could have defined the non-locking composition so that this is considered as an intended deadlock, making the requirement symmetric.
+However the the semantics of composition in a hole is asymmetric and the considered specification -as in the deadlock prevention- is the parent automaton.
 \end{exi}
@@
 We want to prove:
-\begin{multline}
-	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values, \\
-	\sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \tag{WD}\label{eq:drWD}
-\end{multline}
+\[ \forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \tag{WD}\label{eq:drWD} \]
 \[ \bigsymb{\iff} \]
@@
 	\[ \sigma \uplus \nu \vdash \fguard{t_2} \hyp{2'} \]
-	\(R\) satisfies \eqref{eq:drWD} with the current value of \(\mpar{s_1, s_2}\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \nmm{\biguplus_{t_2 \in \fOT{s_2}} \fvars{t_2}} so we have:
+	\(R\) satisfies \eqref{eq:drWD} with the current value of \(\mpar{s_1, s_2}\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \nmm{\biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2}} so we have:
 	\[ \sigma \uplus \nu \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{3} \]
-	The \(\vdash\) hides an implicit \(\exists\) that we use to get values to the variables in \(\biguplus_{t_1 \in \fOT{s_1}} \fvars{t_1}\) in a valuation \(\mu\).
+	The \(\vdash\) hides an implicit \(\exists\) that we use to get values to the variables in \nmm{\biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1}} in a valuation \(\mu\).
 	The left side of the implication is proved using \hyp{1} and \hyp{2'} for the branch \(t_2\) of the disjunction.
@@
 \item[\(\eqref{eq:drWD}\Leftarrow\eqref{eq:drID}\):]
-	Let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \(\sigma: V_1 \uplus V_2 \uplus \biguplus_{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values\).
+	Let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \nmm{\sigma: V_1 \uplus V_2 \uplus \biguplus_{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values}.
 	We want to prove:
@@
 We want to prove
-\[ \forall s \defobject \mpar{s_p, s_c} \in S, \forall \sigma: V \uplus \biguplus_\subbox{t_p \in \fOT{s_p}} \fvars{t_p} \to \values, \sigma \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \tag{WD}\label{eq:nlcWD} \]
+\[ \forall s \defobject \mpar{s_p, s_c} \in S, V \uplus \biguplus_\subbox{t_p \in \fOT{s_p}} \fvars{t_p} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \tag{WD}\label{eq:nlcWD} \]
 \[ \iff \]
@@
 	\[ \sigma \uplus \nu \vdash \fguard{t_p} \hyp{2'} \]
-	\(R\) satisfies \eqref{eq:nlcWD} with the current value of \(s\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \(\biguplus_{t_p \in \fOT{s_p}} \fguard{t_p}\) so we have:
+	\(R\) satisfies \eqref{eq:nlcWD} with the current value of \(s\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \nmm{\biguplus_\subbox{t_p \in \fOT{s_p}} \fvars{t_p}} so we have:
 	\[ \sigma \uplus \nu \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{3} \]
-	The \(\vdash\) hides an implicit \(\exists\) that we use to get values to the variables in \(\biguplus_{t \in \fOT{s}}\) in a valuation \(\mu\).
+	The \(\vdash\) hides an implicit \(\exists\) that we use to get values to the variables in \nmm{\biguplus_\subbox{t \in \fOT{s}} \fvars{t}} in a valuation \(\mu\).
 	The left side of the implication is proved using \hyp{1} and \hyp{2'} for the branch \(t_p\) of the disjunction.
@@
 \item[\(\eqref{eq:nlcWD}\Leftarrow\eqref{eq:nlcID}\):]
-	Let \(s \defobject \mpar{s_p, s_c} \in S\), \(\sigma \in V \uplus \biguplus_{t_p \in \fOT{s_p}} \fvars{t_p} \to \values\).
+	Let \(s \defobject \mpar{s_p, s_c} \in S\), \nmm{\sigma \in V \uplus \biguplus_\subbox{t_p \in \fOT{s_p}} \fvars{t_p} \to \values}.
 	We want to prove:
@@
 	\end{gather}
-	And the current goal is:
-	\[
-		\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\exists} \mpar{t_{3x} \defobject \OTx{3}{x}{3x}{3x} \in \fOT{s_3}}^{x \in X}, \mpar{\forall x \in X, J'_{3x} \cap J_1 = J'_1 \cap J_3} \\[-4pt]
-		\nwedge V_1 \uplus V_3 \uplus \fvars{t_1} \vdash R_{13}\mpar{s_1, s_3} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-			\alpha_1 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x} \cap J_1} \beta_{1j} = \beta_{3xj} \\[12pt]
-			\nwedge g_{3x} \wedge R_{13}\mpar{s'_1, s'_{3x}}\psubst{\psi_1 \uplus \psi_{3x}}
-		\end{array}}
-		\end{array} \goal{0'}
-	\]
 	We use hypothesis \hyp{0} with \(t_1\) for every \(s_2 \in S_2\) to get
@@
 	We pose \nmm{Z \defobject \biguplus_{s_2 \in S_2} \biguplus_{x \in X_{s2}} Z_{s2x}}.
-	We will prove \goal{0'} for the family \(t_{3z}^{z \in Z}\).
+	We will prove \goal{0} for the family \(t_{3z}^{z \in Z}\).
 	The new goals are:
 	\begin{gather}
-		\forall z \in Z, J'_{3z} \cap J_1 = J'_1 \cap J_3 \goal{2} \\
+		\forall z \in Z, J'_{3z} \cap J_1 = J'_1 \cap J_3 \goal{0'} \\
 		V_1 \uplus V_3 \uplus \fvars{t_1} \vdash R_{13}\mpar{s_1, s_3} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{z \in Z} \mpar{\everymath{\displaystyle}\begin{array}{l}
@@
 			\nwedge g_{3z} \wedge R_{13}\mpar{s'_1, s'_{3z}}\psubst{\psi_1 \uplus \psi_{3z}}
-		\end{array}} \goal{3}
+		\end{array}} \goal{2}
 	\end{gather}
-\item[\goal{2}:] By case on \(\triangle\):
+\item[\goal{0'}:] By case on \(\triangle\):
 	\begin{itemize}
@@
 		\end{align*}
-		Hence \goal{2} holds.
 	\item Let \(\triangle\) be \(\supseteq\).
@@
 		\end{align*}
-		Hence \goal{2} holds.
 	\item Let \(\triangle\) be \(=\).
-		We combine the proofs for two above cases and get both inclusions so \goal{2} holds.
+		We combine the proofs for two above cases and get both inclusions so \goal{0'} holds.
 	\end{itemize}
-\item[\goal{3}:] Let \(\sigma_1: V_1 \uplus \fvars{t_1} \to \values\) and \(\sigma_3: V_3 \to \values\).
+\item[\goal{2}:] Let \(\sigma_1: V_1 \uplus \fvars{t_1} \to \values\) and \(\sigma_3: V_3 \to \values\).
 	We use dummy values for variables in \nmm{\biguplus_\subbox{z \in Z} \fvars{t_{3z}}} to get the left side of this implication as an hypothesis (independant from these values):
@@
 	\end{align}
-	Finally to prove \goal{3} with valuation \(\nu_3\) for the implicit \(\exists\), we admit the left side of the implication choose to prove the branch \(z\):
+	Finally to prove \goal{2} with valuation \(\nu_3\) for the implicit \(\exists\), we admit the left side of the implication choose to prove the branch \(z\):
 	\begin{align}
-		\sigma_1 \uplus \sigma_3 \uplus \nu_3 & \vdash \alpha_1 = \alpha_{3z} \goal{3a} \\
-		\sigma_1 \uplus \sigma_3 \uplus \nu_3 & \vdash \bigwedge_\subbox{j \in J'_{3z} \cap J_1} \beta_{1j} = \beta_{3zj} \goal{3b} \\
-		\sigma_3 \uplus \nu_3 & \vdash g_{3z} \goal{3c} \\
-		\sigma_1 \uplus \sigma_3 \uplus \nu_3 &\vdash R_{13}\mpar{s'_1, s'_{3z}}\psubst{\psi_1 \uplus \psi_{3z}} \goal{3d}
+		\sigma_1 \uplus \sigma_3 \uplus \nu_3 & \vdash \alpha_1 = \alpha_{3z} \goal{2a} \\
+		\sigma_1 \uplus \sigma_3 \uplus \nu_3 & \vdash \bigwedge_\subbox{j \in J'_{3z} \cap J_1} \beta_{1j} = \beta_{3zj} \goal{2b} \\
+		\sigma_3 \uplus \nu_3 & \vdash g_{3z} \goal{2c} \\
+		\sigma_1 \uplus \sigma_3 \uplus \nu_3 &\vdash R_{13}\mpar{s'_1, s'_{3z}}\psubst{\psi_1 \uplus \psi_{3z}} \goal{2d}
 	\end{align}
-	\goal{3a} is proved by transitivity using \hyp{5a} and \hyp{5a}.
-	\goal{3b} is proved using \hyp{5b} and \hyp{6b}, but depending on \(\triangle\) the equality are obtained for the interesting values \(j\) using either \hyp{2} and \hyp{2'} or \hyp{3} and \hyp{3'}.
-	\goal{3c} is exactly \hyp{6c}.
-	We prove \goal{3d} with valuation \(\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}\) for the branch \(s_2\) using \hyp{5d} and \hyp{6d}:
+	\goal{2a} is proved by transitivity using \hyp{5a} and \hyp{5a}.
+	\goal{2b} is proved using \hyp{5b} and \hyp{6b}, but depending on \(\triangle\) the equality are obtained for the interesting values \(j\) using either \hyp{2} and \hyp{2'} or \hyp{3} and \hyp{3'}.
+	\goal{2c} is exactly \hyp{6c}.
+	We prove \goal{2d} with valuation \(\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}\) for the branch \(s_2\) using \hyp{5d} and \hyp{6d}:
 	\begin{align*}
@@
 	\begin{gather}
-		\forall s_2 \in \fOT{s_2}, V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{7} \\
-		\forall s_2 \in \fOT{s_2}, V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash R_{23}\mpar{s_2, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{8} \\
+		\forall s_2 \in S_2, V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{7} \\
+		\forall s_2 \in S_2, V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash R_{23}\mpar{s_2, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{8} \\
 		\sigma_1 \uplus \sigma_3 \vdash R_{13}\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{1'}

### 2021-06-09 2021-Refinement/report.tex
Finished proof of theorem 3

@@
 	We pose
-	\[ R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \bigwedge_{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \]
+	\[ R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_1, s_{31}} \wedge \bigwedge_{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \]
 	Where \(y_{3x}\) is the renaming of \(y_3\) from \(A_3\) in \(A_{x3}\).
@@
 \defitem \(J_{13} = J_3 \cup J_1 \setminus \mbrc{k} = J_3 \cup J_2 \setminus \mbrc{k} = J_{23}\) by \(J_1 = J_2\).
-\defitem For \(\sigma_{013} \uplus \sigma_{023} \vdash R\mpar{s_{013}, s_{023}}\) we use the fact that \(R_{12}\) relates inital configurations:
-	\begin{align*}
-		\sigma_{013} \uplus \sigma_{023} \vdash R\mpar{s_{013}, s_{023}} \iff & R\mpar{\mpar{s_{01}, s_{031}}, \mpar{s_{02}, s_{031}}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{031} \uplus \sigma_{032}} \\
-		\iff & R_{12}\mpar{s_{01}, s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02}} \wedge \mpar{\bigwedge_{v_3 \in V_3} v_{31} = v_{32}}\psubst{\sigma_{031} \uplus \sigma_{032}} \\
-		\iff & R_{12}\mpar{s_{01}, s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02}} \wedge \bigwedge_{v_3 \in V_3} \sigma_{031}\mpar{v_{31}} = \sigma_{032}\mpar{v_{32}} \\
-		\iff & R_{12}\mpar{s_{01}, s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02}} \wedge \top \\
-		\iff & \sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}
+\defitem For \(\sigma_{013} \uplus \sigma_{023} \vdash R\mpar{s_{013}, s_{023}}\) we use the fact that \(R_{12}\) relates inital configurations and initial configuration is reachable:
+	\begin{align*}
+		& \sigma_{013} \uplus \sigma_{023} \vdash R\mpar{s_{013}, s_{023}} \\
+		\iff & R\mpar{\mpar{s_{01}, s_{031}}, \mpar{s_{02}, s_{031}}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{031} \uplus \sigma_{032}} \\
+		\iff & R_{12}\mpar{s_{01}, s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}\psubst{\sigma_{013}} \wedge \mpar{\bigwedge_{v_3 \in V_3} v_{31} = v_{32}}\psubst{\sigma_{031} \uplus \sigma_{032}} \\
+		\iff & \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}} \wedge \bigwedge_{v_3 \in V_3} \sigma_{031}\mpar{v_{31}} = \sigma_{032}\mpar{v_{32}} \\
+		\iff & \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}} \wedge \top
 	\end{align*}
@@
 		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{7a} \\
-		\sigma \vdash \bigwedge_{v_3 \in V_3} v_{31} = v_{32} \hyp{7b} \\
-		\sigma \vdash g_{13} \hyp{7c}
+		\sigma \vdash \reach{A_{13}}\mpar{s_{13}} \hyp{7b} \\
+		\sigma \vdash \bigwedge_{v_3 \in V_3} v_{31} = v_{32} \hyp{7c} \\
+		\sigma \vdash g_{13} \hyp{7d}
 	\end{gather}
@@
 	Then we get the values of the implicit \(\exists\) in \nmm{\nu: \biguplus_{x \in X} \fvars{t_{2x}}}.
-	The left side of the implication is proved with \hyp{7a} and \hyp{7c}.
+	The left side of the implication is proved with \hyp{7a} and \hyp{7d}.
 	So we get a \(x \in X\) such that
@@
 		\sigma \uplus \nu \vdash g_{2x} \hyp{8c} \\
-		\sigma \uplus \nu \vdash R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \hyp{8d}
+		\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \hyp{8d}
 	\end{gather}
@@
 	\goal{3b} holds because the valuations for the actions of the holes in \(J_3\) coincide by definition of \(\nu'\) and by \hyp{8b} for the others.
-	For \goal{3c} we have two cases, if \(k \notin J'_1\) then \(g_{23x} \equiv g_{2x}\) and \hyp{8c} is sufficient, if \(k \in J'_1\) then \(g_{23x} \equiv g_{2x} \wedge g_3 \wedge \alpha_3 = \beta_{2xk}\) so we also need \hyp{7c} (\(g_{13} \equiv g_1 \wedge g_3 \wedge \alpha_3 = \beta_{1k}\)) and \hyp{8b} for the value \(k\) (\(\beta_{1k} = \beta_{2xk}\)).
-	\goal{3d} is proved using \hyp{8d} and \hyp{7b}:
+	For \goal{3c} we have two cases, if \(k \notin J'_1\) then \(g_{23x} \equiv g_{2x}\) and \hyp{8c} is sufficient, if \(k \in J'_1\) then \(g_{23x} \equiv g_{2x} \wedge g_3 \wedge \alpha_3 = \beta_{2xk}\) so we also need \hyp{7d} (\(g_{13} \equiv g_1 \wedge g_3 \wedge \alpha_3 = \beta_{1k}\)) and \hyp{8b} for the value \(k\) (\(\beta_{1k} = \beta_{2xk}\)).
+	\goal{3d} is proved using \hyp{8d}, \hyp{7b} with the preservation of reachability across transitions (+ \hyp{7d}), \hyp{7c} and the fact that \(A_3\) performs the same transition with same values in both composed automata:
 	\begin{align*}
 		& \sigma \uplus \nu' \vdash R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}} \\
-		\iff & \sigma \uplus \nu' \vdash \mpar{R_{12}\mpar{s'_1, s'_{2x}} \wedge \bigwedge_{v_3 \in V_3} v_{31} = v_{32}}\psubst{\psi_1 \uplus \psi_{31} \uplus \psi_{2x} \uplus \psi_{32}} \\
-		\iff & \sigma \uplus \nu' \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \bigwedge_{v_3 \in V_3} \psi_{31}\mpar{v_{31}} = \psi_{32}\mpar{v_{32}} \\
-		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \bigwedge_{v_3 \in V_3} v_{31} = v_{32}} & \text{by transport on } \psi_3 \circ \sigma
-	\end{align*}
-\item[\goal{2}:] Let \(\sigma_{13}: V_{13} \to \values\) and \nmm{\sigma_{23}: V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \to \values}.
+		\iff & \sigma \uplus \nu' \vdash \mpar{R_{12}\mpar{s'_1, s'_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}} \wedge \bigwedge_{v_3 \in V_3} v_{31} = v_{32}}\psubst{\psi_1 \uplus \psi_{31} \uplus \psi_{2x} \uplus \psi_{32}} \\
+		\iff & \sigma \uplus \nu' \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}} \wedge \bigwedge_{v_3 \in V_3} \psi_{31}\mpar{v_{31}} = \psi_{32}\mpar{v_{32}} \\
+		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \reach{A_{13}}\mpar{s'_{13}}\psi_{13}} \wedge \mpar{\sigma \vdash \bigwedge_{v_3 \in V_3} v_{31} = v_{32}}
+	\end{align*}
+\item[\goal{2}:] Let \(\sigma: V_{13} \plus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \to \values}.
+	We use dummy values for the variables in \nmm{\biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}}} to get the left side of the implication (independant from dummy values), immediately broken into
+	\begin{gather}
+		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{9a} \\
+		\sigma \vdash \reach{A_{13}}\mpar{s_{13}} \hyp{9b} \\
+		\sigma \vdash \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \hyp{9c}
+	\end{gather}
 	\(R_{12}\) is a simulation and \(\reach{A_{13}}\) witnesses the non-locking simulation so we have the hypothesis:
@@
 		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{10} \\
-		V_1 \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A_{13}}\mpar{s} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{11}
+		V_{13} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A_{13}}\mpar{s} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{11}
 	\end{gather}
-	% TODO: need vars t13 (vars t1 from simu + vars t3 from t23x)
+	We use \hyp{10} with valuation \(\sigma\) projected on the variables from generating transitions in \(A_2\) to get a valuation \nmm{\nu: \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1}}.
+	The left side of the implication is proved using \hyp{9a} and \hyp{9c} because the guards from transitions of \(A_2\) are still in transitions of \(A_{23}\), the right side gives:
+	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{10'} \]
+	We then use \hyp{11} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_13}}.
+	The left side of the implication is proved using \hyp{9b} and \hyp{10'}, the right side gives:
+	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{11'} \]
+	\goal{2} is proved for valuation \(\nu'\) by admitting the left side and using \hyp{11'}.
 \end{proof}
-% Rédiger un paragraphe sur le fait que composer dans l'implem sans deadlock implique qu'il n'y a pas de deadlock quand on compose avec la spec, on voudrais avoirs l'autre sens mais ce n'est pas possible
 \begin{prop}[Composition correctness'] Hole-subset simulation is correct w.r.t.\@ composition with automata without holes. \end{prop}

### 2021-06-10 2021-Refinement/report.tex
Fixed many quick points

@@
 % TODO: CITER LES CONFERENCES
+% TODO: vérifier tous les big([^_]+)_\subbox{[^}]+}[)}]
 
@@
 Section \ref{sec:refinement} introduces and analyses the refinement relation on open automata.
-% flat model
 % future work
@@
 The important properties we consider for the relation on states are being a simulation and the prevention of deadlocks as defined in the following definitions.
-\begin{defi}[Pre-simulation]
+\begin{defi}[Pre-simulation]\label{def:presim}
 For two open automata \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\), a relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a pre-simulation if it satisfies both
@@
 Here we assume that one of the related open automata can be obtained by composing an open automaton in a hole, open automaton which can have holes itself.
-This implies that there is no relation between their holes, for instance composing \(A_i\) in \(j_i\) (\(1 \leq i \leq n\)) of \(A_0\) gives the set of holes \(J \defobject \mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n} \) that is neither subset nor superset of \(J_0\).
+This implies that there is no relation between their holes, for instance composing \(A_i\) in \(j_i\) (\(1 \leq i \leq n\)) of \(A_0\) gives the set of holes \nmm{J \defobject \mpar{\biguplus_\subbox{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}} that is neither subset nor superset of \(J_0\).
 Yet we still assume that in holes with the same name, the same open automaton will be composed.
@@
 In particular if we have a family of open automata \(A_i \defobject \OAg[i]\), \(0 \leq i \leq n\), let \(A \defobject \OAg\) be such that \(A = A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\).
-Recall that there is no relation between the holes of \(A\) and \(A_0\) because \(J = \mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}\) is neither subset nor superset of \(J_0\).
+Recall that there is no relation between the holes of \(A\) and \(A_0\) because \nmm{J = \mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}} is neither subset nor superset of \(J_0\).
 So looking at restricted cases where holes are related in a specific manner can help understanding the general case.
@@
 	\end{array}} \\
-	\wedge V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
+	\wedge \mpar{V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
 \end{multline*}
@@
 The third item of the definition has two parts:
-The first part is the main requirement, a (not equivalent) reordering of the pre-simulation requirement so that it better fits SMT.
+The first part is the main requirement, a (not proved equivalent) reordering of the pre-simulation requirement so that it better fits SMT.
 Instead of matching an effective transition to another effective transition as in the pre-simulation definition, we match an open transition to a family of covering open-transitions.
@@
 
-% TODO: expand on first part, especially the impact of /_\ on the different refinement allowed and what it means, and the fact that = could be substituted with \subseteq.
-
-Examples of application of the different refinement relations are given in appendix \ref{apx:refrel}.
+The hole-equal simulation is applicable when the related automata have the same holes.
+It is designed to capture all the refinements other than composition: Duplicating and merging states and transitions, changing variables, removing transitions, adding requirements to guards, specifying more inital variables, and many more.
+
+The hole-subset simulation is applicable when the simulated automaton has less holes.
+It is designed to have composition correctness when the composed automata have no holes.
+
+The hole-superset simulation is applicable when the simulated automaton has more holes.
+It is designed to capture the addition of holes involved in transitions, which will indirectly add requirements to transitions when the new holes will be composed.
+It is also an attempt at giving a meaning to the new holes when composing with any open automata.
+However it does not capture the removal of holes because other issues arise when trying to both add and remove holes.
+
+Examples of application of the different refinement relations are given in Appendix \ref{apx:refrel}.
 \begin{thm} A hole-\(\triangle\) simulation is a pre-simulation. \end{thm}
-Let \(R\) be a relation on configurations.
-The condition \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\) is in both definitions so proving the following is sufficient:
-\begin{multline}
-	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \\
-	\mpar{\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
-		\quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
-		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}}
-	\end{array}} \hyp{0}
-\end{multline}
-\[ \bigsymb{\implies} \]\vspace{-1cm}
-\begin{multline}
-	\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \forall \sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values, \\
-	\mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \\
-	\sigma \uplus \nu \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \goal{0}
-\end{multline}
-\begin{proof} Let \(\mpar{s_1, s_2} \in S_1 \times S_2\), \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}} and \(\sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values\) be such that
-\[ \sigma \vdash R\mpar{s_1, s_2} \wedge g_1 \hyp{1} \]
-In order to get the transition required to prove
-\begin{multline}
-	\bigsymb{\exists} t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \\
-	\sigma \uplus \nu \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \goal{0'}
-\end{multline}
-we use the hypothesis \hyp{0} with the transition \(t_1\) and get a family of transitions
-\[ \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X} \]
-such that the two following properties hold
-\begin{gather}
-	\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2 \hyp{2} \\
-	V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-		\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
-		\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-	\end{array}} \hyp{3}
-\end{gather}
-\hyp{3} holds for every values of the variables in \(V_1 \uplus V_2 \uplus \fvars{t_1}\) so in particular with the ones given by \(\sigma\).
-We gather the existential variables in a valuation:
-\begin{gather*}
-	\nu: \biguplus_{x \in X} \fvars{t_{2x}} \to \values \\
-	\sigma \uplus \nu \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \bigvee_{x \in X} \mpar{\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x}} \beta_{1j} = \beta_{2xj} \wedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \hyp{4}
-\end{gather*}
-The left side of the implication is proven by \hyp{1}, and we destruct the disjuntion on the right side to get \(x \in X\) and the hypothesis
-\[ \sigma \uplus \nu \vdash \alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \wedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \hyp{4'} \]
-We have \(J'_{2x} \cap J_1 \subseteq J'_{2x}\) and by \hyp{2}, \(J'_{2x} \cap J_1 = J'_1 \cap J_2 \subseteq J'_1\) so \(J'_{2x} \cap J_1 \subseteq J'_{2x} \cap J'_1\).
-Also \(J'_{2x} \cap J'_1 \subseteq J'_{2x} \cap J_1\) because \(J'_1 \subseteq J_1\) by definition of an open transition.
-Hence \(J'_{2x} \cap J_1 = J'_{2x} \cap J'_1\) in \hyp{4'}.
-We can get back to prove \goal{0'} with the transition \(t_{2x}\) and the valuation \(\nu\) by \hyp{4'}.
-\end{proof}
-
+Proof is given in Appendix \ref{apx:presim}.
 \begin{thm} The hole-\(\triangle\) simulation on automata is a preorder. \end{thm}
-Reflexivity is immediate with \(R \defobject \mpar{s, s'} \mapsto \choice{\bigwedge_{v \in V} v_1 = v_2 & s = s'\\ \bot & s \neq s'}\) where \(v_x\) is the renaming to distinguish conflicting automaton variables.
+% TODO: give intuition, then define R on one line then renamin on the line after
+Reflexivity is immediate with \(R \defobject \mpar{s, s'} \mapsto \choice{\bigwedge_{v \in V} v_1 = v_2 & \text{if } s = s'\\ \bot & \text{otherwise}}\) where \(v_x\) is the renaming to distinguish conflicting automaton variables.
 
@@
 The solution is to expand the existential quantifier on states as we did in deadlock prevention, which is possible because states are finite.
-\nmm{R_{13} \defobject \mpar{s_1, s_3} \mapsto \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}} is a witness of the transitivity, proof is given in appendix \ref{apx:trans}.
-\begin{thm}[Context refinement] Hole-equal simulation is context refining \end{thm}
-\begin{proof}
-	For three open automata \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\), let \(k \in J_1\), \(A_{13} \defobject A_1\subst{A_3}{k}\) and \(A_{23} \defobject A_2\subst{A_3}{k}\) with \(A_{13} = \OAg[13]\) and \(A_{23} = \OAg[23]\).
-	Let \(R_{12}\) be a hole-equal simulation of \(A_1\) by \(A_2\) and \(\reach{A_{13}}\) be a witness that \(A_{13}\) is non-locking.
-	The idea for the relation on configurations is that \(A_2\) simulates \(A_1\) while \(A_3\) does the same things in both compositions.
-	We pose
-	\[ R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_1, s_{31}} \wedge \bigwedge_{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \]
-	Where \(y_{3x}\) is the renaming of \(y_3\) from \(A_3\) in \(A_{x3}\).
-	We want to prove that \(R\) is a hole-equal simulation of \(A_{12}\) by \(A_{23}\):
-\defitem \(J_{13} = J_3 \cup J_1 \setminus \mbrc{k} = J_3 \cup J_2 \setminus \mbrc{k} = J_{23}\) by \(J_1 = J_2\).
-\defitem For \(\sigma_{013} \uplus \sigma_{023} \vdash R\mpar{s_{013}, s_{023}}\) we use the fact that \(R_{12}\) relates inital configurations and initial configuration is reachable:
-	\begin{align*}
-		& \sigma_{013} \uplus \sigma_{023} \vdash R\mpar{s_{013}, s_{023}} \\
-		\iff & R\mpar{\mpar{s_{01}, s_{031}}, \mpar{s_{02}, s_{031}}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{031} \uplus \sigma_{032}} \\
-		\iff & R_{12}\mpar{s_{01}, s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}\psubst{\sigma_{013}} \wedge \mpar{\bigwedge_{v_3 \in V_3} v_{31} = v_{32}}\psubst{\sigma_{031} \uplus \sigma_{032}} \\
-		\iff & \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}} \wedge \bigwedge_{v_3 \in V_3} \sigma_{031}\mpar{v_{31}} = \sigma_{032}\mpar{v_{32}} \\
-		\iff & \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}} \wedge \top
-	\end{align*}
-\defitem Let \(s_{13} \defobject \mpar{s_1, s_{31}} \in S_{13}\) and \(s_{23} \defobject \mpar{s_2, s_{32}} \in S_{23}\).
-	We want to prove both
-	\begin{align*}
-		& \bigsymb{\forall} t_{13} \defobject \OTx{13}{}{13}{13} \in \fOT{s_{13}}, \bigsymb{\exists} \mpar{t_{23x} \defobject \OTx{23}{x}{23x}{23x} \in \fOT{s_{23}}}^{x \in X}, \\
-		& \quad \mpar{\forall x \in X, J'_{23x} \cap J_{13} = J'_{13} \cap J_{23}} \\[-10pt]
-		& \nwedge V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \Rightarrow \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\!\!\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \\[12pt]
-			\nwedge g_{23x} \wedge R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
-		\end{array}\!\!} \goal{1}
-	\end{align*}
-	\[ V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash R\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \goal{2} \]
-	Let \nmm{t_{13} \defobject \OTx{13}{}{13}{13} \in \fOT{s_{13}}}, we use the fact that \(R_{12}\) is a simulation from the states \(\mpar{s_1, s_2}\) to get the hypothesis:
-	\begin{align*}
-		& \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
-		& \quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
-		& \nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}} \hyp{5}
-	\end{align*}
-	Transition \(t_{13}\) is obtained in \(A_{13}\) by composition of two transitions \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}} and \nmm{t_3 \defobject \OTx{3}{}{3}{3} \in \fOT{s_3}} if \(k \in J'_1\) or by a the first transition and a fixed state \(s_3 \in S_3\) if \(k \notin J'_1\).
-	We use \hyp{5} with the transition \(t_1\) to get
-	\begin{gather*}
-		\mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X} \\
-		\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2 \hyp{5'} \\
-		V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}} \hyp{5"}
-	\end{gather*}
-	To build the family of transitions we need to know if \(k \in J'_{2x}\) for a every \(x \in X\):
-	\begin{align*}
-		J'_1 & = J'_1 \cap J_1 \\
-		& = J'_1 \cap J_2 & \text{by } J_1 = J_2 \\
-		& = J'_{2x} \cap J_1 & \text{by \hyp{5'}} \\
-		& = J'_{2x} \cap J_2 & \text{by } J_1 = J_2 \\
-		& = J'_{2x} \hyp{6}
-	\end{align*}
-	Using \hyp{6} we can build the familly of transition generated by the family \(t_{2x}^{x \in X}\):
-	\[ t_{23x}^{x \in X} \defobject x \mapsto \choice{
-		\OT{\mpar{s_2, s_3}}{\mpar{s'_{2x}, s'_3}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x} \setminus \mbrc{k}} \uplus \beta_{3j}^{j \in J'_3}}{g_{2x} \wedge g_3 \wedge \alpha_3 = \beta_{2xk}}{\psi_{2x} \uplus \psi_3} & \text{if } k \in J'_{2x} \\
-		\OT{\mpar{s_2, s_3}}{\mpar{s'_{2x}, s_3}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_2}}{g_2}{\psi_2} & \text{if } k \notin J'_{2x}
-	} \]
-	We will prove \goal{1} for the family \(t_{23x}^{x \in X}\), the new goals are
-	\begin{gather}
-		\forall x \in X, J'_{23x} \cap J_{13} = J'_{13} \cap J_{23} \goal{1'} \\
-		V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \\[12pt]
-			\nwedge g_{23x} \wedge R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
-		\end{array}} \goal{3}
-	\end{gather}
-\item[\goal{1'}:] Let \(x \in X\), by case on \(k \in J'_1\):
-	\begin{align*}
-		\text{If } k \in J'_1: && J'_{23x} \cap J_{13} & = \mpar{J'_3 \cup J'_{2x} \setminus \mbrc{k}} \cap \mpar{J_3 \cup J_1 \setminus \mbrc{k}} \\
-		&&& = \mpar{J'_3 \cap J_3} \cup \mpar{J'_{2x} \cap J_1} \setminus \mbrc{k} \\
-		&&& = \mpar{J'_3 \cap J_3} \cup \mpar{J'_1 \cap J_2} \setminus \mbrc{k} & \text{by \hyp{5'}} \\
-		&&& = \mpar{J'_3 \cup J'_1 \setminus \mbrc{k}} \cap \mpar{J_3 \cup J_2 \setminus \mbrc{k}} \\
-		&&& = J'_{13} \cap J_{23} \\
-		\text{If } k \notin J'_1: && J'_{23x} \cap J_{13} & = \mpar{J'_{2x} \setminus \mbrc{k}} \cap \mpar{J_1 \setminus \mbrc{k}} \\
-		&&& = J'_{2x} \cap J_1 & \text{by } k \notin J'_1 = J'_{2x} \text{ \hyp{6}} \\
-		&&& = J'_1 \cap J_2 & \text{by \hyp{5'}} \\
-		&&& = \mpar{J'_1 \setminus \mbrc{k}} \cap \mpar{J_2 \setminus \mbrc{k}} & \text{by } k \notin J'_1 \\
-		&&& = J'_{13} \cap J_{23}
-	\end{align*}
-\item[\goal{3}:] Let \(\sigma: V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \to \values\).
-	We use dummy values for the variables in \nmm{\biguplus_{x \in X} \fvars{t_{23x}}} to get the left side of the implication as an hypothesis (independant from these values):
-	\[ \sigma \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \hyp{7} \]
-	Hypothesis immediately breaken down into
-	\begin{gather}
-		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{7a} \\
-		\sigma \vdash \reach{A_{13}}\mpar{s_{13}} \hyp{7b} \\
-		\sigma \vdash \bigwedge_{v_3 \in V_3} v_{31} = v_{32} \hyp{7c} \\
-		\sigma \vdash g_{13} \hyp{7d}
-	\end{gather}
-	We use \hyp{5"} with valuation \(\sigma\) on variables \(V_1 \uplus V_2 \uplus \fvars{t_1}\), which is possible because the composition of transitions doesn't remove any variable (the simplification steps do, they give bisimilar automata).
-	Then we get the values of the implicit \(\exists\) in \nmm{\nu: \biguplus_{x \in X} \fvars{t_{2x}}}.
-	The left side of the implication is proved with \hyp{7a} and \hyp{7d}.
-	So we get a \(x \in X\) such that
-	\begin{gather}
-		\sigma \uplus \nu \vdash \alpha_1 = \alpha_{2x} \hyp{8a} \\
-		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \hyp{8b} \\
-		\sigma \uplus \nu \vdash g_{2x} \hyp{8c} \\
-		\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \hyp{8d}
-	\end{gather}
-	If \(k \in J'_1\), we extend the valuation \(\nu\) to cover the variables of \(t_3\) in \(t_{23x}\) using their value in \(t_{13}\), \(\nu' \defobject \nu \uplus \mset{v_{32} \mapsto \sigma\mpar{v_{31}}}{v \in \fvars{t_3}}\)
-	Otherwise \(\nu' \defobject \nu\).
-	We progress on \goal{3} by giving the valuation \(\sigma \uplus \nu'\) to the implicit \(\exists\), admitting the left side of the implication and choosing to prove the branch \(x\) of the disjunction:
-	\begin{gather}
-		\sigma \uplus \nu' \vdash \alpha_{13} = \alpha_{23x} \goal{3a} \\
-		\sigma \uplus \nu' \vdash \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \goal{3b} \\
-		\sigma \uplus \nu' \vdash g_{23x} \goal{3c} \\
-		\sigma \uplus \nu' \vdash R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}} \goal{3d}
-	\end{gather}
-	Because composition doesn't change the produced actions nor its variables, \goal{3a} is proved by \hyp{8a}.
-	\goal{3b} holds because the valuations for the actions of the holes in \(J_3\) coincide by definition of \(\nu'\) and by \hyp{8b} for the others.
-	For \goal{3c} we have two cases, if \(k \notin J'_1\) then \(g_{23x} \equiv g_{2x}\) and \hyp{8c} is sufficient, if \(k \in J'_1\) then \(g_{23x} \equiv g_{2x} \wedge g_3 \wedge \alpha_3 = \beta_{2xk}\) so we also need \hyp{7d} (\(g_{13} \equiv g_1 \wedge g_3 \wedge \alpha_3 = \beta_{1k}\)) and \hyp{8b} for the value \(k\) (\(\beta_{1k} = \beta_{2xk}\)).
-	\goal{3d} is proved using \hyp{8d}, \hyp{7b} with the preservation of reachability across transitions (+ \hyp{7d}), \hyp{7c} and the fact that \(A_3\) performs the same transition with same values in both composed automata:
-	\begin{align*}
-		& \sigma \uplus \nu' \vdash R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}} \\
-		\iff & \sigma \uplus \nu' \vdash \mpar{R_{12}\mpar{s'_1, s'_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}} \wedge \bigwedge_{v_3 \in V_3} v_{31} = v_{32}}\psubst{\psi_1 \uplus \psi_{31} \uplus \psi_{2x} \uplus \psi_{32}} \\
-		\iff & \sigma \uplus \nu' \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}} \wedge \bigwedge_{v_3 \in V_3} \psi_{31}\mpar{v_{31}} = \psi_{32}\mpar{v_{32}} \\
-		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \reach{A_{13}}\mpar{s'_{13}}\psi_{13}} \wedge \mpar{\sigma \vdash \bigwedge_{v_3 \in V_3} v_{31} = v_{32}}
-	\end{align*}
-\item[\goal{2}:] Let \(\sigma: V_{13} \plus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \to \values}.
-	We use dummy values for the variables in \nmm{\biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}}} to get the left side of the implication (independant from dummy values), immediately broken into
-	\begin{gather}
-		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{9a} \\
-		\sigma \vdash \reach{A_{13}}\mpar{s_{13}} \hyp{9b} \\
-		\sigma \vdash \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \hyp{9c}
-	\end{gather}
-	\(R_{12}\) is a simulation and \(\reach{A_{13}}\) witnesses the non-locking simulation so we have the hypothesis:
-	\begin{gather}
-		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{10} \\
-		V_{13} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A_{13}}\mpar{s} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{11}
-	\end{gather}
-	We use \hyp{10} with valuation \(\sigma\) projected on the variables from generating transitions in \(A_2\) to get a valuation \nmm{\nu: \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1}}.
-	The left side of the implication is proved using \hyp{9a} and \hyp{9c} because the guards from transitions of \(A_2\) are still in transitions of \(A_{23}\), the right side gives:
-	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{10'} \]
-	We then use \hyp{11} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_13}}.
-	The left side of the implication is proved using \hyp{9b} and \hyp{10'}, the right side gives:
-	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{11'} \]
-	\goal{2} is proved for valuation \(\nu'\) by admitting the left side and using \hyp{11'}.
-\end{proof}
-\begin{prop}[Composition correctness'] Hole-subset simulation is correct w.r.t.\@ composition with automata without holes. \end{prop}
-\begin{proof}
-	Let \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\) be open automata, where \(J_2 = \emptyset\).
-	Let \(k \in J_1\) and \(A \defobject A_1\subst{A_2}{k}\), with \(A = \OAg\).
+\nmm{R_{13} \defobject \mpar{s_1, s_3} \mapsto \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}} is a witness of the transitivity, proof is given in Appendix \ref{apx:trans}.
+\begin{thm}[Context refinement] Hole-equal simulation is context refining. \end{thm}
+For three open automata \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) with \(J_1 = J_2\), let \(k \in J_1\).
+Let \(R_{12}\) be a hole-equal simulation of \(A_1\) by \(A_2\) and \(\reach{A\subst{A_3}{k}}\) be a witness that \(A\subst{A_3}{k}\) is non-locking.
+The idea for the relation on configurations is that \(A_2\) simulates \(A_1\) while \(A_3\) does the same things in both compositions in the hole \(k\).
+\[ R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \]
+Where \(y_{3x}\) is the renaming of \(y_3\) from \(A_3\) in \(A_x\subst{A_3}{k}\).
+\begin{prop}[Limited composition correctness]\label{prop:cc'} Hole-subset simulation is correct w.r.t.\@ composition with automata without holes. \end{prop}
+For two open automata \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\) with \(J_2 = \emptyset\), let \(k \in J_1\) and \(A \defobject A_1\subst{A_2}{k}\), with \(A = \OAg\).
 Let \(\reach{A}\) be a witness that \(A\) is non-locking.
 The idea for the relation on configurations is that the copy of \(A_1\) in \(A\) do the same things as \(A_1\), as if we were trying to prove reflexivity.
-	We pose
-	\[ R \defobject \mpar{\mpar{s_{1'}, s_2}, s_1} \mapsto \choice{\bigwedge_{v_1 \in V_1} v_{1'} = v_1 & \text{if } s_{1'} = s_1 \\ \bot & \text{otherwise}} \]
+\[ R \defobject \mpar{\mpar{s_{1'}, s_2}, s_1} \mapsto \choice{\reach{A}\mpar{s_{1'}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1 & \text{if } s_{1'} = s_1 \\ \bot & \text{otherwise}} \]
 Where \(y_{1'}\) is the renaming of \(y_1\) from \(A_1\) in \(A\).
-	We want to prove that \(R\) is a hole-subset simulation of \(A\) by \(A_1\):
-	\begin{gather}
-		J_2 \cup J_1 \setminus \mbrc{k} \subseteq J_1 \goal{5a} \\
-		\sigma_0 \uplus \sigma_{01} \vdash R\mpar{s_0, s_{01}} \goal{5b}
-	\end{gather}\vspace{-1cm}
-	\begin{multline}
-		\forall \mpar{s, s_1} \in S \times S_1, \\
-		\mpar{\everymath{\displaystyle}\begin{array}{l}
-			\bigsymb{\forall} t \defobject \OTg \in \fOT{s}, \bigsymb{\exists} \mpar{t_{1x} \defobject \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X}, \\
-			\quad \mpar{\forall x \in X, J'_{1x} \cap J = J' \cap J_1} \\[-10pt]
-			\nwedge V \uplus V_1 \uplus \fvars{t} \vdash R\mpar{s, s_1} \wedge g \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-				\alpha = \alpha_{1x} \wedge \bigwedge_\subbox{j \in J'_{1x} \cap J} \beta_j = \beta_{1xj} \\[12pt]
-				\nwedge g_{1x} \wedge R\mpar{s', s'_{1x}}\psubst{\psi \uplus \psi_{1x}}
-			\end{array}}
-		\end{array}} \\
-		\wedge V \uplus V_1 \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash R\mpar{s, s_1} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \goal{5c}
-	\end{multline}
-	\goal{5a} is easy because \(J_2 = \emptyset\).
-	For \goal{5b} we use the fact that we don't constrain the behaviour of \(J_2\):
-	\begin{align*}
-		\sigma_0 \uplus \sigma_{01} \vdash R\mpar{s_0, s_{01}} \iff & \mpar{\bigwedge_{v_1 \in V_1} v_{1'} = v_1}\psubst{\sigma_{01'} \uplus \sigma_{02} \uplus \sigma_{01}} \\
-		\iff & \bigwedge_{v_1 \in V_1} \sigma_{01'}\mpar{v_{1'}} = \sigma_{01}\mpar{v_1} \\
-		\iff & \top
-	\end{align*}
-	Let \(s \defobject \mpar{s_{1'}, s_2} \in S\) and \(s_1 \in S_1\).
-	The goals left to prove are
-	\begin{align*}
-		& \bigsymb{\forall} t \defobject \OTg \in \fOT{s}, \bigsymb{\exists} \mpar{t_{1x} \defobject \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X}, \\
-		& \quad \mpar{\forall x \in X, J'_{1x} \cap J = J' \cap J_1} \\[-10pt]
-		& \nwedge V \uplus V_1 \uplus \fvars{t} \vdash R\mpar{s, s_1} \wedge g \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha = \alpha_{1x} \wedge \bigwedge_\subbox{j \in J'_{1x} \cap J} \beta_j = \beta_{1xj} \\[12pt]
-			\nwedge g_{1x} \wedge R\mpar{s', s'_{1x}}\psubst{\psi \uplus \psi_{1x}}
-		\end{array}} \goal{6}
-	\end{align*}
-	\[ V \uplus V_1 \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash R\mpar{s, s_1} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \goal{7} \]
-\item[\goal{6}:] % TODO: proove each goal
-\item[\goal{7}:] % TODO: proove each goal
-\end{proof}
-\begin{prop}[Composition correctness"]
+\begin{prop}[Special composition correctness]
 Let \(A_1 \defobject \OAg[1]\) be hole-superset simulated by \(A_2 \defobject \OAg[2]\).
@@
 \end{prop}
-\begin{proof}
-% TODO
-\end{proof}
+Proofs of the above theorem and propositions are given in Appendix \ref{apx:ophts}.
+
 % J'2 \subseteq J'1 in hole-subset, J'1 \subseteq J'2 in hole-superset (decide of transition variable with holes); composition with new holes is hole-subset where hole variables are free then hole-superset where hole names have no conflicts with removed holes.
@@
 \section{Refinement relation for open automata}\label{sec:refinement}
-% meaning of f, what happens depending on f
-% hole function from implem to spec on disjoint holes
 \begin{defi}[Open automata refinement]
@@
 
-\section{Example of composition}\label{apx:composition}
+\section{Example of composition}
+
+\subsection{Complete composition}\label{apx:composition}
 \begin{figure}[h]
@@
 
-\section{Example of deadlock introduced by composition and requirements of non-locking composition}\label{apx:lockcomp}
+\subsection{Composition introducing deadlocks and requirements of non-locking composition}\label{apx:lockcomp}
 \begin{exi}[Deadlocks introduced by composition]
@@
 	However we cannot yet prove it because we don't know whether \(t_2\) and \(t_1\) match.
-	In order to get a \(t_2\) matching \(t_1\) we will use the fact that \(R\) is a pre-simulation.
+	In order to get a \(t_2\) matching \(t_1\) we will use the fact that \(R\) is a \hyperref[def:presim]{pre-simulation}:
 	\begin{multline}
@@
 		\mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \\
-		\sigma \uplus \nu \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \hyp{sim}
+		\sigma \uplus \nu \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \hyp{0}
 	\end{multline}
-	\hyp{sim} with current value of \(\mpar{s_1, s_2}\), \(t_1\) and \(\sigma \uplus \mu\) as a valuation of \(V_1 \uplus V_2 \uplus \fvars{t_1}\) gives:
+	\hyp{0} with current value of \(\mpar{s_1, s_2}\), \(t_1\) and \(\sigma \uplus \mu\) as a valuation of \(V_1 \uplus V_2 \uplus \fvars{t_1}\) gives:
 	\begin{multline}
@@
 \item[\(\eqref{eq:drWD}\Leftarrow\eqref{eq:drID}\):]
-	Let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \nmm{\sigma: V_1 \uplus V_2 \uplus \biguplus_{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values}.
+	Let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \nmm{\sigma: V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values}.
 	We want to prove:
@@
 \[ \forall s \defobject \mpar{s_p, s_c} \in S, V \uplus \biguplus_\subbox{t_p \in \fOT{s_p}} \fvars{t_p} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \tag{WD}\label{eq:nlcWD} \]
-\[ \iff \]
+\[ \bigsymb{\iff} \]
 \begin{multline*}
@@
 	\[ \sigma \uplus \nu \vdash \fguard{t_p} \hyp{2'} \]
-	\(R\) satisfies \eqref{eq:nlcWD} with the current value of \(s\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \nmm{\biguplus_\subbox{t_p \in \fOT{s_p}} \fvars{t_p}} so we have:
+	\(\reach{A}\) satisfies \eqref{eq:nlcWD} with the current value of \(s\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \nmm{\biguplus_\subbox{t_p \in \fOT{s_p}} \fvars{t_p}} so we have:
 	\[ \sigma \uplus \nu \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{3} \]
-	The \(\vdash\) hides an implicit \(\exists\) that we use to get values to the variables in \nmm{\biguplus_\subbox{t \in \fOT{s}} \fvars{t}} in a valuation \(\mu\).
+	The \(\vdash\) hides an implicit \(\exists\) that we use to get \nmm{\mu: \biguplus_\subbox{t \in \fOT{s}} \fvars{t} \to \values}.
 	The left side of the implication is proved using \hyp{1} and \hyp{2'} for the branch \(t_p\) of the disjunction.
@@
 \item[\(\eqref{eq:nlcWD}\Leftarrow\eqref{eq:nlcID}\):]
-	Let \(s \defobject \mpar{s_p, s_c} \in S\), \nmm{\sigma \in V \uplus \biguplus_\subbox{t_p \in \fOT{s_p}} \fvars{t_p} \to \values}.
+	Let \(s \defobject \mpar{s_p, s_c} \in S\), \nmm{\sigma: V \uplus \biguplus_\subbox{t_p \in \fOT{s_p}} \fvars{t_p} \to \values}.
 	We want to prove:
@@
 \section{Examples of hole-\(\triangle\) simulations}\label{apx:refrel}
+
 \subsection{Example of hole-equal simulation}
@@
 \end{figure}
-To illustrate the definition and the different refinement operations, Figure \ref{fig:hisim} introduces two related open automata with same holes \(\mbrc{l, r}\).
+Figure \ref{fig:hisim} introduces two related open automata with same holes \(\mbrc{l, r}\).
 The automaton on the left is a parallel composition: any hole can perform actions at any time, the actions are passed unmodified and no synchronisation is performed.
 The automaton on the right is a sequential composition with \(n\) control switches: a hole performs a sequence of actions then the other does, there are \(n\) seqences of a single automaton doing actions without the other performing some.
-The initial valuation of the right automaton is in blue, actually we want to consider both the automaton with this initial valuation and the one without.
 
 Intuitively the right automaton is a refinement of the left automaton because the left automaton is what happens when there was no bound \(n\) in the right automaton.
-Also the right automaton with the initial valuation is a refinement of the right automaton with the initial valuation because a ``\(1\) control switches" is an instance of a ``\(n\) control switches".
-
-First let consider \(R\), a hole-identical simulation of \(n\) control switches by parallel composition:
 \[ R \defobject \mbrc{\mpar{l, ||} \mapsto \top, \mpar{r, ||} \mapsto \top} \]
-% TODO: continue
+\(R\) is a hole-identical simulation of \(n\) control switches by parallel composition.
+There are enough examples of proofs of refinement in this article for the reader to be able to prove it as an exercise.
 \end{exi}
 
-% Hole-subset: Traffic lights
-% Hole-superset: scheduler
-
-% APB
+\subsection{Example of hole-subset simulation}
+Example of Appendix \ref{apx:composition} can be reused here.
+The automaton on Figure \ref{fig:tlf} is a refinement of the one on Figure \ref{fig:tls} by limited composition correctness (Proposition \ref{prop:cc'}).
+
+It is a simplified version of the motivation for making a refinement relation, which is the traffic light system in an article about weak-bisimulation \cite{wang:03126313}.
+It had to be modified because here the simulation is a strong-simulation.
+
+\subsection{Example of hole-superset simulation}
+% TODO: vending machine of the presentation + money module
+
+\section{Proofs of properties for hole-\(\triangle\) simulation}\label{apx:ophts}
+
+\subsection{Hole-\(\triangle\) simulation is a pre-simulation}\label{apx:presim}
+Let \(R\) be a relation on configurations.
+The condition \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\) is in both definitions and the deadlock prevention requirement will not be used so proving the following is sufficient:
+\begin{multline}
+	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \\
+	\mpar{\everymath{\displaystyle}\begin{array}{l}
+		\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
+		\quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
+		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
+			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}}
+	\end{array}} \hyp{0}
+\end{multline}
+\[ \bigsymb{\implies} \]\vspace{-1cm}
+\begin{multline}
+	\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \forall \sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values, \\
+	\mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \\
+	\sigma \uplus \nu \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \goal{0}
+\end{multline}
+\begin{proof} Let \(\mpar{s_1, s_2} \in S_1 \times S_2\), \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}} and \(\sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values\) be such that
+\[ \sigma \vdash R\mpar{s_1, s_2} \wedge g_1 \hyp{1} \]
+In order to get the transition required to prove
+\begin{multline}
+	\bigsymb{\exists} t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \\
+	\sigma \uplus \nu \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \goal{0'}
+\end{multline}
+we use the hypothesis \hyp{0} with the transition \(t_1\) and get a family of transitions
+\[ \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X} \]
+such that the two following properties hold
+\begin{gather}
+	\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2 \hyp{2} \\
+	V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+		\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
+		\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+	\end{array}} \hyp{3}
+\end{gather}
+\hyp{3} holds for every values of the variables in \(V_1 \uplus V_2 \uplus \fvars{t_1}\) so in particular with the ones given by \(\sigma\).
+We gather the variables of the implicit \(\exists\) in a valuation \nmm{\nu: \biguplus_{x \in X} \fvars{t_{2x}} \to \values}.
+\[ \sigma \uplus \nu \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \bigvee_{x \in X} \mpar{\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \wedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \hyp{3'} \]
+The left side of the implication is proved by \hyp{1}, and for the right side we get \(x \in X\) such that
+\[ \sigma \uplus \nu \vdash \alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \wedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \hyp{4} \]
+% TODO: put that on several lines using a math env
+We have \(J'_{2x} \cap J_1 \subseteq J'_{2x}\) and by \hyp{2}, \(J'_{2x} \cap J_1 = J'_1 \cap J_2 \subseteq J'_1\) so \(J'_{2x} \cap J_1 \subseteq J'_{2x} \cap J'_1\).
+Also \(J'_{2x} \cap J'_1 \subseteq J'_{2x} \cap J_1\) because \(J'_1 \subseteq J_1\) by definition of an open transition.
+Hence \(J'_{2x} \cap J_1 = J'_{2x} \cap J'_1\) in \hyp{4}.
+We can get back to prove \goal{0'} with the transition \(t_{2x}\) and the valuation \(\nu\) by \hyp{4}.
+\end{proof}
+
+\subsection{Context refinement for hole-equal simulation}
+Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) be three pen automata.
+Let \(k \in J_1\), \(A_{13} \defobject A_1\subst{A_3}{k}\) and \(A_{23} \defobject A_2\subst{A_3}{k}\) with \(A_{13} = \OAg[13]\) and \(A_{23} = \OAg[23]\).
+Let \(R_{12}\) be a hole-equal simulation of \(A_1\) by \(A_2\) and \(\reach{A_{13}}\) be a witness that \(A_{13}\) is non-locking.
+\[ R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \]
+Where \(y_{3x}\) is the renaming of \(y_3\) from \(A_3\) in \(A_{x3}\).
+We want to prove that \(R\) is a hole-equal simulation of \(A_{12}\) by \(A_{23}\).
+\begin{proof}
+\defitem \(J_{13} = J_3 \cup J_1 \setminus \mbrc{k} = J_3 \cup J_2 \setminus \mbrc{k} = J_{23}\) by \(J_1 = J_2\).
+\defitem For \(\sigma_{013} \uplus \sigma_{023} \vdash R\mpar{s_{013}, s_{023}}\) we use the fact that \(R_{12}\) relates inital configurations and initial configuration is reachable:
+	\begin{align*}
+		& \sigma_{013} \uplus \sigma_{023} \vdash R\mpar{s_{013}, s_{023}} \\
+		\iff & R\mpar{\mpar{s_{01}, s_{031}}, \mpar{s_{02}, s_{031}}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{031} \uplus \sigma_{032}} \\
+		\iff & R_{12}\mpar{s_{01}, s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}\psubst{\sigma_{013}} \wedge \mpar{\bigwedge_{v_3 \in V_3} v_{31} = v_{32}}\psubst{\sigma_{031} \uplus \sigma_{032}} \\
+		\iff & \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}} \wedge \bigwedge_\subbox{v_3 \in V_3} \sigma_{031}\mpar{v_{31}} = \sigma_{032}\mpar{v_{32}} \\
+		\iff & \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}} \wedge \top
+	\end{align*}
+\defitem Let \(s_{13} \defobject \mpar{s_1, s_{31}} \in S_{13}\) and \(s_{23} \defobject \mpar{s_2, s_{32}} \in S_{23}\).
+	We want to prove both
+	\begin{align*}
+		& \bigsymb{\forall} t_{13} \defobject \OTx{13}{}{13}{13} \in \fOT{s_{13}}, \bigsymb{\exists} \mpar{t_{23x} \defobject \OTx{23}{x}{23x}{23x} \in \fOT{s_{23}}}^{x \in X}, \\
+		& \quad \mpar{\forall x \in X, J'_{23x} \cap J_{13} = J'_{13} \cap J_{23}} \\[-10pt]
+		& \nwedge V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \Rightarrow \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\!\!\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \\[12pt]
+			\nwedge g_{23x} \wedge R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
+		\end{array}\!\!} \goal{0}
+	\end{align*}
+	\[ V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash R\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \goal{1} \]
+	Let \nmm{t_{13} \defobject \OTx{13}{}{13}{13} \in \fOT{s_{13}}}, we use the fact that \(R_{12}\) is a simulation from the states \(\mpar{s_1, s_2}\) to get the hypothesis:
+	\begin{align*}
+		& \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
+		& \quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
+		& \nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
+			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}} \hyp{1}
+	\end{align*}
+	Transition \(t_{13}\) is obtained in \(A_{13}\) by composition of two transitions \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}} and \nmm{t_{31} \defobject \OTx{31}{}{31}{31} \in \fOT{s_{31}}} if \(k \in J'_1\) or by a the first transition and a fixed state \(s_{31}\) if \(k \notin J'_1\).
+	We use \hyp{1} with the transition \(t_1\) to get
+	\begin{gather*}
+		\mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X} \\
+		\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2 \hyp{1'} \\
+		V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
+			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}} \hyp{1"}
+	\end{gather*}
+	To build the family of transitions we need to know if \(k \in J'_{2x}\) for a every \(x \in X\):
+	\begin{align*}
+		J'_1 & = J'_1 \cap J_1 \\
+		& = J'_1 \cap J_2 & \text{by } J_1 = J_2 \\
+		& = J'_{2x} \cap J_1 & \text{by \hyp{1'}} \\
+		& = J'_{2x} \cap J_2 & \text{by } J_1 = J_2 \\
+		& = J'_{2x} \hyp{2}
+	\end{align*}
+	In the case \(s_{31} \neq s_{32}\) we can give the empty family, it won't cause any issue.
+	Otherwise \(s_{31} = s_{32}\) so we can copy \(t_{31}\) into \nmm{t_{32} = \OTx{32}{}{32}{32}} to avoid conflicts.
+	We also name \(t_3\) the original transition from \(T_3\).
+	Using \hyp{2} we can build the familly of transition generated by the family \(t_{2x}^{x \in X}\):
+	\[ t_{23x}^{x \in X} \defobject x \mapsto \choice{
+		\OT{\mpar{s_2, s_{32}}}{\mpar{s'_{2x}, s'_{32}}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x} \setminus \mbrc{k}} \uplus \beta_{3j}^{j \in J'_{32}}}{g_{2x} \wedge g_{32} \wedge \alpha_{32} = \beta_{2xk}}{\psi_{2x} \uplus \psi_{32}} & \text{if } k \in J'_{2x} \\
+		\OT{\mpar{s_2, s_{32}}}{\mpar{s'_{2x}, s_{32}}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_2}}{g_2}{\psi_2} & \text{otherwise}
+	} \label{eq:t23x} \]
+	We will prove \goal{0} for the family \(t_{23x}^{x \in X}\), the new goals are
+	\begin{gather}
+		\forall x \in X, J'_{23x} \cap J_{13} = J'_{13} \cap J_{23} \goal{0'} \\
+		V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \\[12pt]
+			\nwedge g_{23x} \wedge R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
+		\end{array}} \goal{2}
+	\end{gather}
+\item[\goal{0'}:] Let \(x \in X\), by case on \(k \in J'_1\):
+	\begin{align*}
+		\text{If } k \in J'_1: && J'_{23x} \cap J_{13} & = \mpar{J'_{31} \cup J'_{2x} \setminus \mbrc{k}} \cap \mpar{J_3 \cup J_1 \setminus \mbrc{k}} \\
+		&&& = \mpar{J'_{31} \cap J_3} \cup \mpar{J'_{2x} \cap J_1} \setminus \mbrc{k} \\
+		&&& = \mpar{J'_{31} \cap J_3} \cup \mpar{J'_1 \cap J_2} \setminus \mbrc{k} & \text{by \hyp{1'}} \\
+		&&& = \mpar{J'_{31} \cup J'_1 \setminus \mbrc{k}} \cap \mpar{J_3 \cup J_2 \setminus \mbrc{k}} \\
+		&&& = J'_{13} \cap J_{23} \\
+		\text{If } k \notin J'_1: && J'_{23x} \cap J_{13} & = \mpar{J'_{2x} \setminus \mbrc{k}} \cap \mpar{J_1 \setminus \mbrc{k}} \\
+		&&& = J'_{2x} \cap J_1 & \text{by } k \notin J'_1 = J'_{2x} \text{ \hyp{2}} \\
+		&&& = J'_1 \cap J_2 & \text{by \hyp{1'}} \\
+		&&& = \mpar{J'_1 \setminus \mbrc{k}} \cap \mpar{J_2 \setminus \mbrc{k}} & \text{by } k \notin J'_1 \\
+		&&& = J'_{13} \cap J_{23}
+	\end{align*}
+\item[\goal{2}:] Let \(\sigma: V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \to \values\).
+	We use dummy values for the variables in \nmm{\biguplus_{x \in X} \fvars{t_{23x}}} to get the left side of the implication as an hypothesis (independant from these values):
+	\[ \sigma \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \hyp{3} \]
+	If \(s_{31} \neq s_{32}\) then this hypothesis is \(\sigma \vdash \bot\), the empty family works and the proof is finished.
+	We can assume \(s_{31} = s_{32}\) and the family given \hyperref[eq:t23x]{previously} works.
+	We break \hyp{3} into
+	\begin{gather}
+		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{3a} \\
+		\sigma \vdash \reach{A_{13}}\mpar{s_{13}} \hyp{3b} \\
+		\sigma \vdash \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} \hyp{3c} \\
+		\sigma \vdash g_{13} \hyp{3d}
+	\end{gather}
+	We use \hyp{1"} with valuation \(\sigma\) on variables \(V_1 \uplus V_2 \uplus \fvars{t_1}\), which is possible because the composition of transitions doesn't remove any variable (the simplification steps do, they give bisimilar automata).
+	Then we get the values of the implicit \(\exists\) in \nmm{\nu: \biguplus_{x \in X} \fvars{t_{2x}}}.
+	The left side of the implication is proved with \hyp{3a} and \hyp{3d}.
+	So we get a \(x \in X\) such that
+	\begin{gather}
+		\sigma \uplus \nu \vdash \alpha_1 = \alpha_{2x} \hyp{4a} \\
+		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \hyp{4b} \\
+		\sigma \uplus \nu \vdash g_{2x} \hyp{4c} \\
+		\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \hyp{4d}
+	\end{gather}
+	If \(k \in J'_1\), we extend the valuation \(\nu\) to cover the variables of \(t_3\) in \(t_{23x}\) using their value in \(t_{13}\), \(\nu' \defobject \nu \uplus \mset{v_{32} \mapsto \sigma\mpar{v_{31}}}{v_3 \in \fvars{t_3}}\)
+	Otherwise \(\nu' \defobject \nu\).
+	We progress on \goal{2} by giving the valuation \(\sigma \uplus \nu'\) to the implicit \(\exists\), admitting the left side of the implication and choosing to prove the branch \(x\) of the disjunction:
+	\begin{gather}
+		\sigma \uplus \nu' \vdash \alpha_{13} = \alpha_{23x} \goal{3a} \\
+		\sigma \uplus \nu' \vdash \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \goal{3b} \\
+		\sigma \uplus \nu' \vdash g_{23x} \goal{3c} \\
+		\sigma \uplus \nu' \vdash R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}} \goal{3d}
+	\end{gather}
+	Because composition doesn't change the produced actions nor its variables, \goal{3a} is proved by \hyp{4a}.
+	\goal{3b} holds because the valuations for the actions of the holes in \(J_3\) coincide by definition of \(\nu'\) and by \hyp{4b} for the others.
+	For \goal{3c} we have two cases, if \(k \notin J'_1\) then \(g_{23x} \equiv g_{2x}\) and \hyp{4c} is sufficient, if \(k \in J'_1\) then \(g_{23x} \equiv g_{2x} \wedge g_3 \wedge \alpha_3 = \beta_{2xk}\) so we also need \hyp{3d} (\(g_{13} \equiv g_1 \wedge g_3 \wedge \alpha_3 = \beta_{1k}\)) and \hyp{4b} for the value \(k\) (\(\beta_{1k} = \beta_{2xk}\)).
+	\goal{3d} is proved using \hyp{4d}, \hyp{3b} with the preservation of reachability across transitions (+ \hyp{3d}), \hyp{3c} and the fact that \(A_3\) performs the same transition with same values in both composed automata:
+	\begin{align*}
+		& \sigma \uplus \nu' \vdash R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}} \\
+		\iff & \sigma \uplus \nu' \vdash \mpar{R_{12}\mpar{s'_1, s'_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32}}\psubst{\psi_1 \uplus \psi_{31} \uplus \psi_{2x} \uplus \psi_{32}} \\
+		\iff & \sigma \uplus \nu' \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}} \wedge \bigwedge_\subbox{v_3 \in V_3} \psi_{31}\mpar{v_{31}} = \psi_{32}\mpar{v_{32}} \\
+		\iff & \sigma \uplus \nu' \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}} \wedge \bigwedge_\subbox{v_3 \in V_3 \cup \fvars{t_3}} v_{31} = v_{32} \\
+		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \reach{A_{13}}\mpar{s'_{13}}\psi_{13}} \wedge \mpar{\sigma \vdash \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32}}
+	\end{align*}
+\item[\goal{1}:] Let \nmm{\sigma: V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \to \values}.
+	We use dummy values for the variables in \nmm{\biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}}} to get the left side of the implication (independant from dummy values), immediately broken into
+	\begin{gather}
+		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{5a} \\
+		\sigma \vdash \reach{A_{13}}\mpar{s_{13}} \hyp{5b} \\
+		\sigma \vdash \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \hyp{5c}
+	\end{gather}
+	\(R_{12}\) is a simulation and \(\reach{A_{13}}\) witnesses the non-locking simulation so we have the hypothesis:
+	\begin{gather}
+		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6} \\
+		V_{13} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A_{13}}\mpar{s} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{7}
+	\end{gather}
+	We use \hyp{6} with valuation \(\sigma\) projected on the variables from generating transitions in \(A_2\) to get \nmm{\nu: \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
+	The left side of the implication is proved using \hyp{5a} and \hyp{5c} because the guards from transitions of \(A_2\) are still in transitions of \(A_{23}\), the right side gives:
+	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6'} \]
+	We then use \hyp{7} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}}}.
+	The left side of the implication is proved using \hyp{5b} and \hyp{6'}, the right side gives:
+	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{7'} \]
+	\goal{1} is proved for valuation \(\nu'\) by admitting the left side and using \hyp{7'}.
+\end{proof}
+
+\subsection{Limited composition correctness for hole-subset simulation}
+Let \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\) be open automata, where \(J_2 = \emptyset\).
+Let \(k \in J_1\) and \(A \defobject A_1\subst{A_2}{k}\), with \(A = \OAg\).
+Let \(\reach{A}\) be a witness that \(A\) is non-locking.
+\[ R \defobject \mpar{\mpar{s_{1'}, s_2}, s_1} \mapsto \choice{\reach{A}\mpar{s_{1'}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1 & \text{if } s_{1'} = s_1 \\ \bot & \text{otherwise}} \]
+Where \(y_{1'}\) is the renaming of \(y_1\) from \(A_1\) in \(A\).
+We want to prove that \(R\) is a hole-subset simulation of \(A\) by \(A_1\):
+\begin{proof}
+\defitem \(J = J_2 \cup J_1 \setminus \mbrc{k} = \emptyset \cup J_1 \setminus \mbrc{k} \subseteq J_1\)
+\defitem We use the fact that \(R\) doesn't constrain the behaviour of \(J_2\):
+	\begin{align*}
+		\sigma_0 \uplus \sigma_{01} \vdash R\mpar{s_0, s_{01}} \iff & \mpar{\bigwedge_{v_1 \in V_1} v_{1'} = v_1}\psubst{\sigma_{01'} \uplus \sigma_{02} \uplus \sigma_{01}} \\
+		\iff & \bigwedge_\subbox{v_1 \in V_1} \sigma_{01'}\mpar{v_{1'}} = \sigma_{01}\mpar{v_1} \\
+		\iff & \top
+	\end{align*}
+\defitem Let \(s \defobject \mpar{s_{1'}, s_2} \in S\) and \(s_1 \in S_1\).
+	We want to prove both
+	\begin{align*}
+		& \bigsymb{\forall} t \defobject \OTg \in \fOT{s}, \bigsymb{\exists} \mpar{t_{1x} \defobject \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X}, \\
+		& \quad \mpar{\forall x \in X, J'_{1x} \cap J = J' \cap J_1} \\[-10pt]
+		& \nwedge V \uplus V_1 \uplus \fvars{t} \vdash R\mpar{s, s_1} \wedge g \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha = \alpha_{1x} \wedge \bigwedge_\subbox{j \in J'_{1x} \cap J} \beta_j = \beta_{1xj} \\[12pt]
+			\nwedge g_{1x} \wedge R\mpar{s', s'_{1x}}\psubst{\psi \uplus \psi_{1x}}
+		\end{array}} \goal{0}
+	\end{align*}
+	\[ V \uplus V_1 \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash R\mpar{s, s_1} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \goal{1} \]
+	Let \nmm{t \defobject \OTg \in \fOT{s}}, we know that \(t\) is obtained by composition so there is a generating transition \(t_1 \in \fOT{s_1}\) for which we will prove \goal{0}.
+	If \(s_{1'} \neq s_1\) we instead prove \goal{0} with the empty family.
+	\begin{gather}
+		\forall x \in X, J'_1 \cap J = J' \cap J_1 \goal{0'} \\
+		V \uplus V_1 \uplus \fvars{t} \vdash R\mpar{s, s_1} \wedge g \implies \alpha = \alpha_1 \wedge \bigwedge_\subbox{j \in J'_1 \cap J} \beta_j = \beta_{1j} \wedge g_1 \wedge R\mpar{s', s'_1}\psubst{\psi \uplus \psi_1} \goal{2}
+	\end{gather}
+\item[\goal{0'}:] \(t\) is a transition built from \(t_1\) so it has its holes.
+	Additionnally either \(k \notin J'_1\) so \(J' = J'_1\) or \(k \in J'_1\) so \(J' = \emptyset \cup J'_1 \setminus \mbrc{k}\) because \(A_2\) has no holes.
+	Either case \(J'_1 \cap J = J'_1 \setminus \mbrc{k} = \mpar{J'_1 \setminus \mbrc{k}} \cap J_1 = J' \cap J_1\).
+\item[\goal{2}:] Let \(\sigma: V \uplus V_1 \uplus \fvars{t} \to \values\).
+	We rename some variables in the input domain of \(\sigma\) to get \(\nu: \fvars{t_1} \to \values\).
+	We use \(\nu\) to prove \goal{2}, get the left side of the implication as an hypothesis and break the right side of the implication:
+	\begin{gather}
+		\sigma \vdash R\mpar{s, s_1} \wedge g \hyp{1} \\
+		\sigma \uplus \nu \vdash \alpha = \alpha_1 \goal{2a} \\
+		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_1 \cap J} \beta_j = \beta_{1j} \goal{2b} \\
+		\sigma \uplus \nu \vdash g_1 \goal{2c} \\
+		\sigma \uplus \nu \vdash R\mpar{s', s'_1}\psubst{\psi \uplus \psi_1} \goal{2d}
+	\end{gather}
+	If \(s_{1'} \neq s_1\) then \hyp{1} is \(\sigma \vdash \bot\) so the proof is finished and the empty family worked.
+	Otherwise we can assume \(s_{1'} = s_1\) and break \hyp{1} into
+	\begin{gather}
+		\sigma \vdash \reach{A}\mpar{s} \hyp{1a} \\
+		\sigma \vdash \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1 \hyp{1b} \\
+		\sigma \vdash g \hyp{1c}
+	\end{gather}
+	\goal{2a} holds because composition doesn't change the produced action and the valuation coincide on the renamed variables.
+	\goal{2b} also holds because \(J'_1 \cap J = J'_1 \setminus \mbrc{k} = J'\), composition doesn't change the actions of the holes involved and the valuation coincide on the renamed variables.
+	\goal{2c} is proved using \hyp{1c} (\(g \equiv g_1\) or \(g \equiv g_1 \wedge \dots\)).
+	For \goal{2d} we use \hyp{1a} with the preservation of reachability across transitions (+ \hyp{1b}), \hyp{1b} and the fact that the valuations coincide on the renamed values:
+	\begin{align*}
+		& \sigma \uplus \nu \vdash R\mpar{s', s'_1}\psubst{\psi \uplus \psi_1} \\
+		\iff & \sigma \uplus \nu \vdash \mpar{\reach{A}\mpar{s} \wedge \bigwedge_{v_1 \in V_1} v_{1'} = v_1}\psubst{\psi \uplus \psi_1} \\
+		\iff & \sigma \uplus \nu \vdash \reach{A}\mpar{s}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1} \psi_{1'}\mpar{v_{1'}} = \psi\mpar{v_1} \\
+		\iff & \sigma \uplus \nu \vdash \reach{A}\mpar{s}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1 \cup \fvars{t_1}} v_{1'} = v_1 \\
+		\iff & \mpar{\sigma \vdash \reach{A}\mpar{s}\psubst{\psi}} \wedge \mpar{\sigma \uplus \nu \vdash \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1}
+	\end{align*}
+\item[\goal{1}:] % TODO: adapt and continue
+	Let \nmm{\sigma: V \uplus V_1 \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
+	We rename some variables in the input domain of \(\sigma\) to get \(\nu: \fvars{t_1} \to \values\).
+\end{proof}
+
+\subsection{Special composition correctness for hole-superset simulation}
+\begin{proof}
+% TODO
+\end{proof}
 
@@
 	\[ \sigma_1 \uplus \sigma_3 \vdash R_{13}\mpar{s_1, s_3} \wedge g_1 \hyp{4} \]
-	Hypothesis that we immediately break down into
+	Hypothesis immediately broken down into
 	\begin{gather*}
@@
 	\end{align}
-	We can now use \hyp{1x'} with valuation \(\sigma_2 \uplus \nu_2 \uplus \sigma_3\) to get \nmm{\nu_3: \biguplus_{Z \in Z_{s2x}} \fvars{t_{3z}} \to \values}.
+	We can now use \hyp{1x'} with valuation \(\sigma_2 \uplus \nu_2 \uplus \sigma_3\) to get \nmm{\nu_3: \biguplus_\subbox{Z \in Z_{s2x}} \fvars{t_{3z}} \to \values}.
 	The left side of the implication is proved with the left side of \hyp{4'} and \hyp{4"}, so we get \(z \in Z_{s2x}\) and the hypotheses
@@
 	\end{gather*}
-	We can use immediately \hyp{8} with state \(s_2\) and valuation \(\sigma_2 \uplus \sigma_3\) to get \nmm{\nu_2: \biguplus_{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values}.
+	We can use immediately \hyp{8} with state \(s_2\) and valuation \(\sigma_2 \uplus \sigma_3\) to get \nmm{\nu_2: \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values}.
 	The left side of the implication is proved with the right side of \hyp{9'} and \hyp{9"}, so we get
 	\[ \sigma_3 \uplus \nu_2 \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{8'} \]
-	We can now use \hyp{7} with state \(s_2\) and valuation \(\sigma_1 \uplus \sigma_2 \uplus \nu_2\) to get \nmm{\nu_1: \biguplus_{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
+	We can now use \hyp{7} with state \(s_2\) and valuation \(\sigma_1 \uplus \sigma_2 \uplus \nu_2\) to get \nmm{\nu_1: \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
 	The left side of the implication is proved with the left side of \hyp{9'} and \hyp{8'}, so we get

### 2021-06-10 2021-Refinement/report.tex
Proof consistency

@@
 % TODO: CITER LES CONFERENCES
-% TODO: vérifier tous les big([^_]+)_\subbox{[^}]+}[)}]
 
@@
 The important properties we consider for the relation on states are being a simulation and the prevention of deadlocks as defined in the following definitions.
-\begin{defi}[Pre-simulation]\label{def:presim}
+\begin{defi}[Pre-simulation]
 For two open automata \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\), a relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a pre-simulation if it satisfies both
@@
 Here we assume that one of the related open automata can be obtained by composing an open automaton in a hole, open automaton which can have holes itself.
-This implies that there is no relation between their holes, for instance composing \(A_i\) in \(j_i\) (\(1 \leq i \leq n\)) of \(A_0\) gives the set of holes \nmm{J \defobject \mpar{\biguplus_\subbox{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}} that is neither subset nor superset of \(J_0\).
+This implies that there is no relation between their holes, for instance composing \(A_i\) in \(j_i\) (\(1 \leq i \leq n\)) of \(A_0\) gives the set of holes \(J \defobject \mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}\) that is neither subset nor superset of \(J_0\).
 Yet we still assume that in holes with the same name, the same open automaton will be composed.
@@
 In particular if we have a family of open automata \(A_i \defobject \OAg[i]\), \(0 \leq i \leq n\), let \(A \defobject \OAg\) be such that \(A = A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\).
-Recall that there is no relation between the holes of \(A\) and \(A_0\) because \nmm{J = \mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}} is neither subset nor superset of \(J_0\).
+Recall that there is no relation between the holes of \(A\) and \(A_0\) because \(J = \mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}\) is neither subset nor superset of \(J_0\).
 So looking at restricted cases where holes are related in a specific manner can help understanding the general case.
@@
 For two open automata \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\triangle\) simulation of \(A_1\) by \(A_2\) if:
-\defitem \(J_1 \triangle J_2\)
-\defitem \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
-\defitem \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)\vspace{-8pt}
+\item[1)] \(J_1 \triangle J_2\)
+\item[2)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
+\item[3)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)\vspace{-8pt}
 \noindent\begin{multline*}
@@
 \begin{thm} The hole-\(\triangle\) simulation on automata is a preorder. \end{thm}
-% TODO: give intuition, then define R on one line then renamin on the line after
-Reflexivity is immediate with \(R \defobject \mpar{s, s'} \mapsto \choice{\bigwedge_{v \in V} v_1 = v_2 & \text{if } s = s'\\ \bot & \text{otherwise}}\) where \(v_x\) is the renaming to distinguish conflicting automaton variables.
-
-For three open automata \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\), such that \(R_{12}\) is a hole-\(\triangle\) simulation of \(A_1\) by \(A_2\) and \(R_{23}\) of \(A_2\) by \(A_3\), we want to define \(R_{13}\) by saying that there exists a state \(s_2 \in S_2\) and values for \(V_2\) such that \(R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}\).
+The idea for reflexivity is that the related automata are always in the same configuration.
+\[ R \defobject \mpar{s, s'} \mapsto \choice{\bigwedge_{v \in V} v_1 = v_2 & \text{if } s = s'\\ \bot & \text{otherwise}} \]
+Where \(v_x\) is the renaming to distinguish conflicting automaton variables.
+\(R\) is a witness of the reflexivity, the proof is mainly the same as several of the following ones so it will be omitted.
+
+For three open automata \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\), such that \(R_{12}\) is a hole-\(\triangle\) simulation of \(A_1\) by \(A_2\) and \(R_{23}\) of \(A_2\) by \(A_3\), we want to define \(R\) by saying that there exists a state \(s_2 \in S_2\) and values for \(V_2\) such that \(R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}\).
 However we cannot talk about states in formulas.
 The solution is to expand the existential quantifier on states as we did in deadlock prevention, which is possible because states are finite.
-\nmm{R_{13} \defobject \mpar{s_1, s_3} \mapsto \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}} is a witness of the transitivity, proof is given in Appendix \ref{apx:trans}.
+\[ R \defobject \mpar{s_1, s_3} \mapsto \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \]
+\(R\) is a witness of the transitivity, proof is given in Appendix \ref{apx:trans}.
 \begin{thm}[Context refinement] Hole-equal simulation is context refining. \end{thm}
@@
 Where \(y_{3x}\) is the renaming of \(y_3\) from \(A_3\) in \(A_x\subst{A_3}{k}\).
+\(R\) is a witness of the context refinement.
 \begin{prop}[Limited composition correctness]\label{prop:cc'} Hole-subset simulation is correct w.r.t.\@ composition with automata without holes. \end{prop}
-For two open automata \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\) with \(J_2 = \emptyset\), let \(k \in J_1\) and \(A \defobject A_1\subst{A_2}{k}\), with \(A = \OAg\).
+For two open automata \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\) with \(J_2 = \emptyset\), let \(k \in J_1\) and \(A \defobject A_1\subst{A_2}{k}\).
 Let \(\reach{A}\) be a witness that \(A\) is non-locking.
@@
 Where \(y_{1'}\) is the renaming of \(y_1\) from \(A_1\) in \(A\).
+\(R\) is a witness of the limited composition correctness.
 \begin{prop}[Special composition correctness]
-Let \(A_1 \defobject \OAg[1]\) be hole-superset simulated by \(A_2 \defobject \OAg[2]\).
-Let \(j \in J_1 \setminus J_2\) and \(A_3\) an open automaton.
-There is a hole-superset simulation of \(A_1\subst{A_3}{j}\) by \(A_2\).
+For three open automata \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\), let \(k \in J_1 \setminus J_2\) and \(R_{12}\) be a hole-superset simulation of \(A_1\) by \(A_2\).
+There is a hole-superset simulation of \(A_1\subst{A_3}{k}\) by \(A_2\).
 \end{prop}
+Let \(\reach{A_1\subst{A_3}{k}}\) be a witness that \(A_1\subst{A_3}{k}\) is non-locking.
+The idea for the relation on configurations is to combine the non-locking composition and the already existing realtion on configurations.
+\[ R \defobject \mpar{\mpar{s_1, s_3}, s_2} \mapsto R_{12}\mpar{s_1, s_2} \wedge \reach{A_1\subst{A_3}{k}}\mpar{s_1, s_3} \]
+\(R\) is a witness of the secial composition correctness.
 Proofs of the above theorem and propositions are given in Appendix \ref{apx:ophts}.
@@
 \begin{exi}[Deadlocks introduced by composition]
-\Ludo{TODOludo}{lire l'explication}
 This example reuses the counter introduced in Figure \ref{fig:tlh}.
@@
 	However we cannot yet prove it because we don't know whether \(t_2\) and \(t_1\) match.
-	In order to get a \(t_2\) matching \(t_1\) we will use the fact that \(R\) is a \hyperref[def:presim]{pre-simulation}:
+	In order to get a \(t_2\) matching \(t_1\) we will use the fact that \(R\) is a pre-simulation:
 	\begin{multline}
@@
 \[ \sigma \uplus \nu \vdash \alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \wedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \hyp{4} \]
-% TODO: put that on several lines using a math env
-We have \(J'_{2x} \cap J_1 \subseteq J'_{2x}\) and by \hyp{2}, \(J'_{2x} \cap J_1 = J'_1 \cap J_2 \subseteq J'_1\) so \(J'_{2x} \cap J_1 \subseteq J'_{2x} \cap J'_1\).
-Also \(J'_{2x} \cap J'_1 \subseteq J'_{2x} \cap J_1\) because \(J'_1 \subseteq J_1\) by definition of an open transition.
-Hence \(J'_{2x} \cap J_1 = J'_{2x} \cap J'_1\) in \hyp{4}.
-We can get back to prove \goal{0'} with the transition \(t_{2x}\) and the valuation \(\nu\) by \hyp{4}.
+We have \(J'_{2x} \cap J_1 = J'_{2x} \cap J'_1\) in \hyp{4}:
+\begin{align*}
+	J'_{2x} \cap J_1 & \subseteq J'_{2x} \tag{1} \\
+	J'_{2x} \cap J_1 & = J'_1 \cap J_2 & \text{by \hyp{2}} \\
+	& \subseteq J'_1 \tag{2} \\
+	J'_{2x} \cap J_1 & \subseteq J'_{2x} \cap J'_1 & \text{by (1) and (2)} \tag{3} \\
+	J'_{2x} \cap J'_1 & \subseteq J'_{2x} \cap J_1 & \text{by } J'_1 \subseteq J_1 \tag{4} \\
+	J'_{2x} \cap J_1 & = J'_{2x} \cap J'_1 & \text{by (3) and (4)}
+\end{align*}
+So we can prove \goal{0'} for the transition \(t_{2x}\) and the valuation \(\nu\) by \hyp{4}.
 \end{proof}
@@
 \subsection{Context refinement for hole-equal simulation}
-Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) be three pen automata.
+Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) be three open automata.
 Let \(k \in J_1\), \(A_{13} \defobject A_1\subst{A_3}{k}\) and \(A_{23} \defobject A_2\subst{A_3}{k}\) with \(A_{13} = \OAg[13]\) and \(A_{23} = \OAg[23]\).
@@
 \begin{proof}
-\defitem \(J_{13} = J_3 \cup J_1 \setminus \mbrc{k} = J_3 \cup J_2 \setminus \mbrc{k} = J_{23}\) by \(J_1 = J_2\).
-\defitem For \(\sigma_{013} \uplus \sigma_{023} \vdash R\mpar{s_{013}, s_{023}}\) we use the fact that \(R_{12}\) relates inital configurations and initial configuration is reachable:
+\item[1)] \(J_{13} = J_3 \cup J_1 \setminus \mbrc{k} = J_3 \cup J_2 \setminus \mbrc{k} = J_{23}\) by \(J_1 = J_2\).
+\item[2)] For \(\sigma_{013} \uplus \sigma_{023} \vdash R\mpar{s_{013}, s_{023}}\) we use the fact that \(R_{12}\) relates inital configurations and initial configuration is reachable:
 	\begin{align*}
@@
 	\end{align*}
-\defitem Let \(s_{13} \defobject \mpar{s_1, s_{31}} \in S_{13}\) and \(s_{23} \defobject \mpar{s_2, s_{32}} \in S_{23}\).
+\item[3)] Let \(s_{13} \defobject \mpar{s_1, s_{31}} \in S_{13}\) and \(s_{23} \defobject \mpar{s_2, s_{32}} \in S_{23}\).
 	We want to prove both
@@
 		\OT{\mpar{s_2, s_{32}}}{\mpar{s'_{2x}, s_{32}}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_2}}{g_2}{\psi_2} & \text{otherwise}
-	} \label{eq:t23x} \]
+	} \]
 	We will prove \goal{0} for the family \(t_{23x}^{x \in X}\), the new goals are
@@
 	If \(s_{31} \neq s_{32}\) then this hypothesis is \(\sigma \vdash \bot\), the empty family works and the proof is finished.
-	We can assume \(s_{31} = s_{32}\) and the family given \hyperref[eq:t23x]{previously} works.
-	We break \hyp{3} into
+	We can assume \(s_{31} = s_{32}\) and break \hyp{3} into
 	\begin{gather}
@@
 \item[\goal{1}:] Let \nmm{\sigma: V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \to \values}.
-	We use dummy values for the variables in \nmm{\biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}}} to get the left side of the implication (independant from dummy values), immediately broken into
+	We use dummy values for the variables in \nmm{\biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}}} to get the left side of the implication (independant from these values), immediately broken into
 	\begin{gather}
@@
 	\end{gather}
-	\(R_{12}\) is a simulation and \(\reach{A_{13}}\) witnesses the non-locking simulation so we have the hypothesis:
+	\(R_{12}\) is a simulation and \(\reach{A_{13}}\) witnesses the non-locking composition so we have the hypotheses:
 	\begin{gather}
 		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6} \\
-		V_{13} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A_{13}}\mpar{s} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{7}
+		V_{13} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{7}
 	\end{gather}
@@
 Where \(y_{1'}\) is the renaming of \(y_1\) from \(A_1\) in \(A\).
-We want to prove that \(R\) is a hole-subset simulation of \(A\) by \(A_1\):
+We want to prove that \(R\) is a hole-subset simulation of \(A\) by \(A_1\).
 \begin{proof}
-\defitem \(J = J_2 \cup J_1 \setminus \mbrc{k} = \emptyset \cup J_1 \setminus \mbrc{k} \subseteq J_1\)
-\defitem We use the fact that \(R\) doesn't constrain the behaviour of \(J_2\):
+\item[1)] \(J = J_2 \cup J_1 \setminus \mbrc{k} = \emptyset \cup J_1 \setminus \mbrc{k} \subseteq J_1\)
+\item[2)] We use the fact that \(R\) doesn't constrain the behaviour of \(J_2\):
 	\begin{align*}
@@
 	\end{align*}
-\defitem Let \(s \defobject \mpar{s_{1'}, s_2} \in S\) and \(s_1 \in S_1\).
+\item[3)] Let \(s \defobject \mpar{s_{1'}, s_2} \in S\) and \(s_1 \in S_1\).
 	We want to prove both
@@
 	Let \nmm{\sigma: V \uplus V_1 \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
-	We rename some variables in the input domain of \(\sigma\) to get \(\nu: \fvars{t_1} \to \values\).
+	We use dummy values for the variables in \nmm{\biguplus_\subbox{t \in \fOT{s}} \fvars{t}} to get the left side of the implication (independant from these values), immediately broken into
+	\begin{gather}
+		\sigma \vdash \reach{A}\mpar{s} \hyp{2a} \\
+		\sigma \vdash \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1 \hyp{2b} \\
+		\sigma \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{2c}
+	\end{gather}
+	\(\reach{A}\) is a witness of the non-locking composition so we have the hypothesis:
+	\[ V \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{3} \]
+	We use \hyp{3} with valuation \(\sigma\) to get \nmm{\nu: \biguplus_\subbox{t \in \fOT{s}} \fvars{t} \to \values}.
+	The left side of the implication is proved with \hyp{2a} and \hyp{2c}, the right side gives the hypothesis:
+	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{3'} \]
+	We prove \goal{1} with valuation \(\nu\) by admitting the left side ofthe implication and using \hyp{3}.
 \end{proof}
@@
 \subsection{Special composition correctness for hole-superset simulation}
+Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and  \(A_3 \defobject \OAg[3]\) be open automata.
+Let \(k \in J_1 \setminus J_2\) and \(A \defobject A_1\subst{A_3}{k}\), with \(A = \OAg\).
+Let \(R_{12}\) be a hole-superset simulation of \(A_1\) by \(A_2\) and \(\reach{A}\) be a witness that \(A\) is non-locking.
+\[ R \defobject \mpar{\mpar{s_1, s_3}, s_2} \mapsto R_{12}\mpar{s_1, s_2} \wedge \reach{A_1\subst{A_3}{k}}\mpar{s_1, s_3} \]
+We want to prove that \(R\) is a hole-superset simulation of \(A\) by \(A_2\).
 \begin{proof}
-% TODO
+\item[1)] % TODO
+\item[2)] % TODO
+\item[3)] % TODO
 \end{proof}
@@
 Let \(R_{12}\) be a hole-\(\triangle\) simulation of \(A_1\) by \(A_2\) and \(R_{23}\) of \(A_2\) by \(A_3\).
-\[ R_{13} \defobject \mpar{s_1, s_3} \mapsto \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \]
-\(R_{13}\) is a hole-\(\triangle\) simulation of \(A_1\) by \(A_3\).
+\[ R \defobject \mpar{s_1, s_3} \mapsto \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \]
+We want to prove that \(R\) is a hole-\(\triangle\) simulation of \(A_1\) by \(A_3\).
 \begin{proof}
-\defitem By transitivity of \(\triangle\), \(J_1 \triangle J_3\)
-\defitem We prove that initial configurations are related using \(\sigma_{02}\) as the values of the variables in \(V_2\), and \(s_{02}\) to choose the branch of the disjunction.
-\begin{align*}
-	\sigma_{01} \uplus \sigma_{03} \vdash R_{13}\mpar{s_{01}, s_{03}} \iff & \sigma_{01} \uplus \sigma_{03} \vdash \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_{01}, s_2} \wedge R_{23}\mpar{s_2, s_{03}} \\
+\item[1)] By transitivity of \(\triangle\), \(J_1 \triangle J_3\)
+\item[2)] We prove that initial configurations are related using \(\sigma_{02}\) as the values of the variables in \(V_2\), and \(s_{02}\) to choose the branch of the disjunction.
+\begin{align*}
+	\sigma_{01} \uplus \sigma_{03} \vdash R\mpar{s_{01}, s_{03}} \iff & \sigma_{01} \uplus \sigma_{03} \vdash \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_{01}, s_2} \wedge R_{23}\mpar{s_2, s_{03}} \\
 	\impliedby & \sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03} \vdash R_{12}\mpar{s_{01}, s_{02}} \wedge R_{23}\mpar{s_{02}, s_{03}} \\
@@
 \end{align*}
-\defitem Let \(\mpar{s_1, s_3} \in S_1 \times S_3\), we want to prove both
+\item[3)] Let \(\mpar{s_1, s_3} \in S_1 \times S_3\), we want to prove both
 	\begin{align*}
@@
 		& \mpar{\forall x \in X, J'_{3x} \cap J_1 = J'_1 \cap J_3} \\[-10pt]
-		& \wedge V_1 \uplus V_3 \uplus \fvars{t_1} \vdash R_{13}\mpar{s_1, s_3} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+		& \wedge V_1 \uplus V_3 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_3} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
 			\alpha_1 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x} \cap J_1} \beta_{1j} = \beta_{3xj} \\[12pt]
-			\nwedge g_{3x} \wedge R_{13}\mpar{s'_1, s'_{3x}}\psubst{\psi_1 \uplus \psi_{3x}}
+			\nwedge g_{3x} \wedge R\mpar{s'_1, s'_{3x}}\psubst{\psi_1 \uplus \psi_{3x}}
 		\end{array}} \goal{0}
 	\end{align*}
-	\[ V_1 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash R_{13}\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{1} \]
+	\[ V_1 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash R\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{1} \]
 \item[\goal{0}:] Let \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}}.
@@
 		\forall z \in Z, J'_{3z} \cap J_1 = J'_1 \cap J_3 \goal{0'} \\
-		V_1 \uplus V_3 \uplus \fvars{t_1} \vdash R_{13}\mpar{s_1, s_3} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{z \in Z} \mpar{\everymath{\displaystyle}\begin{array}{l}
+		V_1 \uplus V_3 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_3} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{z \in Z} \mpar{\everymath{\displaystyle}\begin{array}{l}
 			\alpha_1 = \alpha_{3z} \wedge \bigwedge_\subbox{j \in J'_{3z} \cap J_1} \beta_{1j} = \beta_{3zj} \\[12pt]
-			\nwedge g_{3z} \wedge R_{13}\mpar{s'_1, s'_{3z}}\psubst{\psi_1 \uplus \psi_{3z}}
+			\nwedge g_{3z} \wedge R\mpar{s'_1, s'_{3z}}\psubst{\psi_1 \uplus \psi_{3z}}
 		\end{array}} \goal{2}
@@
 	We use dummy values for variables in \nmm{\biguplus_\subbox{z \in Z} \fvars{t_{3z}}} to get the left side of this implication as an hypothesis (independant from these values):
-	\[ \sigma_1 \uplus \sigma_3 \vdash R_{13}\mpar{s_1, s_3} \wedge g_1 \hyp{4} \]
+	\[ \sigma_1 \uplus \sigma_3 \vdash R\mpar{s_1, s_3} \wedge g_1 \hyp{4} \]
 	Hypothesis immediately broken down into
@@
 		\sigma_3 \uplus \nu_3 & \vdash g_{3z} \goal{2c} \\
-		\sigma_1 \uplus \sigma_3 \uplus \nu_3 &\vdash R_{13}\mpar{s'_1, s'_{3z}}\psubst{\psi_1 \uplus \psi_{3z}} \goal{2d}
+		\sigma_1 \uplus \sigma_3 \uplus \nu_3 &\vdash R\mpar{s'_1, s'_{3z}}\psubst{\psi_1 \uplus \psi_{3z}} \goal{2d}
 	\end{align}
@@
 	\begin{align*}
-		& \sigma_1 \uplus \sigma_3 \uplus \nu_3 \vdash R_{13}\mpar{s'_1, s'_{3z}}\psubst{\psi_1 \uplus \psi_{3z}} \\
+		& \sigma_1 \uplus \sigma_3 \uplus \nu_3 \vdash R\mpar{s'_1, s'_{3z}}\psubst{\psi_1 \uplus \psi_{3z}} \\
 		\iff & \mpar{R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}}\psubst{\psi_1 \uplus \psi_{3z}}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_1 \uplus \sigma_3 \uplus \nu_3} \\
@@
 		\forall s_2 \in S_2, V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash R_{23}\mpar{s_2, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{8} \\
-		\sigma_1 \uplus \sigma_3 \vdash R_{13}\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{1'}
+		\sigma_1 \uplus \sigma_3 \vdash R\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{1'}
 	\end{gather}
 	We use dummy values for variables in \nmm{\biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1}} to get the left side of this implication as an hypothesis (independant from these values):
-	\[ \sigma_1 \uplus \sigma_3 \vdash R_{13}\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \hyp{9} \]
+	\[ \sigma_1 \uplus \sigma_3 \vdash R\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \hyp{9} \]
 	Hypothesis that we immediately break down into:

### 2021-06-12 2021-Refinement/report.tex
Document margins and proof of Proposition 3

@@
 \usepackage{fontspec}
-\usepackage[hmargin=0.5in,marginparwidth=1.5in,includemp]{geometry}
+\usepackage[hmargin=3cm]{geometry}
 \usepackage{amsmath}
@@
 % TODO: CITER LES CONFERENCES
+% TODO: verify cup -> uplus, tell that uplus is disjoint union
 
@@
 
-The contributions of this article are the definition of composition for open automata without having to define open pNets, and the introduciton of several refinement relations for open automata\marginpar{TODO: expand}.
+The contributions of this article are the definition of composition for open automata without having to define open pNets, and the introduciton of several refinement relations for open automata.
+% TODO: expand
 
@@
 
-The terms \(\terms\) is a term algebra\marginpar{reference to come}.
+The terms \(\terms\) is a term algebra.
 As any term algebra it has constant symbols with arity, variables, and a typing mechanism to distinguish well-formed and ill-formed terms.
@@
 \begin{defi}[Relation on configurations]
-A relation on configurations of two open automata \(\OAg[1]\) and \(\OAg[2]\) is a function \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
+A relation on configurations of \(\OAg[1]\) and \(\OAg[2]\) is a function \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
 
@@
 \begin{defi}[Pre-simulation]
-For two open automata \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\), a relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a pre-simulation if it satisfies both
+Let \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\).
+A relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a pre-simulation if it satisfies both
 \defitem Initial configurations are related: \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\);
@@
 \end{defi}
-This definition translated to open automata the classical definition of simulation \marginpar{cite: Fernandez-Mounier-91-b}.
+This definition translated to open automata the classical definition of simulation \cite{10.1007/3-540-54430-5_78}.
 The last formula means that for every pair of related configurations of the automaton and every possible transitions (\(\vdash g_1\)) from the first automaton, there is a possible transition (\(\vdash g_2\)) such that the produced action matches (\(\alpha_1 = \alpha_2\)), the same holes' action (\(J'_1 \cap J'_2\)) matches (\(\beta_{1j} = \beta_{2j}\)) and the target states are related after variable update.
@@
 
-For three open automata \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\), such that \(R_{12}\) is a hole-\(\triangle\) simulation of \(A_1\) by \(A_2\) and \(R_{23}\) of \(A_2\) by \(A_3\), we want to define \(R\) by saying that there exists a state \(s_2 \in S_2\) and values for \(V_2\) such that \(R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}\).
+Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\).
+Let \(R_{12}\) be a hole-\(\triangle\) simulation of \(A_1\) by \(A_2\) and \(R_{23}\) of \(A_2\) by \(A_3\), we want to define \(R\) by saying that there exists a state \(s_2 \in S_2\) and values for \(V_2\) such that \(R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}\).
 However we cannot talk about states in formulas.
@@
 \begin{thm}[Context refinement] Hole-equal simulation is context refining. \end{thm}
-For three open automata \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) with \(J_1 = J_2\), let \(k \in J_1\).
-Let \(R_{12}\) be a hole-equal simulation of \(A_1\) by \(A_2\) and \(\reach{A\subst{A_3}{k}}\) be a witness that \(A\subst{A_3}{k}\) is non-locking.
+Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) with \(J_1 = J_2\).
+Let \(k \in J_1\), \(R_{12}\) be a hole-equal simulation of \(A_1\) by \(A_2\) and \(\reach{A\subst{A_3}{k}}\) be a witness that \(A\subst{A_3}{k}\) is non-locking.
 The idea for the relation on configurations is that \(A_2\) simulates \(A_1\) while \(A_3\) does the same things in both compositions in the hole \(k\).
@@
 Where \(y_{3x}\) is the renaming of \(y_3\) from \(A_3\) in \(A_x\subst{A_3}{k}\).
-\(R\) is a witness of the context refinement.
+\(R\) is a witness of the context refinement, proof is given in Appendix \ref{apx:crhe}.
 \begin{prop}[Limited composition correctness]\label{prop:cc'} Hole-subset simulation is correct w.r.t.\@ composition with automata without holes. \end{prop}
@@
 Where \(y_{1'}\) is the renaming of \(y_1\) from \(A_1\) in \(A\).
-\(R\) is a witness of the limited composition correctness.
+\(R\) is a witness of the limited composition correctness, proof is given in Appendix \ref{apx:lchs}.
 \begin{prop}[Special composition correctness]
-For three open automata \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\), let \(k \in J_1 \setminus J_2\) and \(R_{12}\) be a hole-superset simulation of \(A_1\) by \(A_2\).
+For three open automata \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3\), let \(k \in J_1 \setminus J_2\) and \(R_{12}\) be a hole-superset simulation of \(A_1\) by \(A_2\).
 There is a hole-superset simulation of \(A_1\subst{A_3}{k}\) by \(A_2\).
@@
 \[ R \defobject \mpar{\mpar{s_1, s_3}, s_2} \mapsto R_{12}\mpar{s_1, s_2} \wedge \reach{A_1\subst{A_3}{k}}\mpar{s_1, s_3} \]
-\(R\) is a witness of the secial composition correctness.
-Proofs of the above theorem and propositions are given in Appendix \ref{apx:ophts}.
-
+\(R\) is a witness of the secial composition correctness, proof is given in Appendix \ref{apx:schs}.
+
+% TODO HERE
 % J'2 \subseteq J'1 in hole-subset, J'1 \subseteq J'2 in hole-superset (decide of transition variable with holes); composition with new holes is hole-subset where hole variables are free then hole-superset where hole names have no conflicts with removed holes.
@@
 
-% Mettre des sets de noms en commun qu'on veut effectivement mapper pour la transitivité
 % Explain what happens on holes constraints and action constraints
@@
 \section{Refinement relation for open automata}\label{sec:refinement}
+% TODO: intro
 \begin{defi}[Open automata refinement]
@@
 
-\section{Proofs of properties for hole-\(\triangle\) simulation}\label{apx:ophts}
+\section{Proofs of properties for hole-\(\triangle\) simulation}
 
@@
 \end{align*}
-So we can prove \goal{0'} for the transition \(t_{2x}\) and the valuation \(\nu\) by \hyp{4}.
+So we can prove \goal{0'} for the transition \(t_{2x}\) and the valuation \(\nu\) using \hyp{4}.
 \end{proof}
 
-\subsection{Context refinement for hole-equal simulation}
+\subsection{Context refinement for hole-equal simulation}\label{apx:crhe}
 Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) be three open automata.
-Let \(k \in J_1\), \(A_{13} \defobject A_1\subst{A_3}{k}\) and \(A_{23} \defobject A_2\subst{A_3}{k}\) with \(A_{13} = \OAg[13]\) and \(A_{23} = \OAg[23]\).
+Let \(k \in J_1\), \(A_{13} \defobject A_1\subst{A_3}{k}\) and \(A_{23} \defobject A_2\subst{A_3}{k}\).
 Let \(R_{12}\) be a hole-equal simulation of \(A_1\) by \(A_2\) and \(\reach{A_{13}}\) be a witness that \(A_{13}\) is non-locking.
+We pose \(A_{13} = \OAg[13]\) and \(A_{23} = \OAg[23]\).
 \[ R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \]
@@
 	\end{align*}
-	Transition \(t_{13}\) is obtained in \(A_{13}\) by composition of two transitions \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}} and \nmm{t_{31} \defobject \OTx{31}{}{31}{31} \in \fOT{s_{31}}} if \(k \in J'_1\) or by a the first transition and a fixed state \(s_{31}\) if \(k \notin J'_1\).
+	Transition \(t_{13}\) is obtained in \(A_{13}\) by composition of two transitions \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}} and \nmm{t_{31} \defobject \OTx{31}{}{31}{31} \in \fOT{s_{31}}} if \(k \in J'_1\) or by a the first transition and the state \(s_{31}\) if \(k \notin J'_1\).
 	We use \hyp{1} with the transition \(t_1\) to get
@@
 		\iff & \sigma \uplus \nu' \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}} \wedge \bigwedge_\subbox{v_3 \in V_3 \cup \fvars{t_3}} v_{31} = v_{32} \\
-		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \reach{A_{13}}\mpar{s'_{13}}\psi_{13}} \wedge \mpar{\sigma \vdash \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32}}
+		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}}} \wedge \mpar{\sigma \vdash \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32}}
 	\end{align*}
@@
 	\end{gather}
-	\(R_{12}\) is a simulation and \(\reach{A_{13}}\) witnesses the non-locking composition so we have the hypotheses:
+	\(R_{12}\) is a simulation and \(\reach{A_{13}}\) is a witness of the non-locking composition so we have the hypotheses:
 	\begin{gather}
@@
 
-\subsection{Limited composition correctness for hole-subset simulation}
+\subsection{Limited composition correctness for hole-subset simulation}\label{apx:lchs}
 Let \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\) be open automata, where \(J_2 = \emptyset\).
@@
 \item[1)] \(J = J_2 \cup J_1 \setminus \mbrc{k} = \emptyset \cup J_1 \setminus \mbrc{k} \subseteq J_1\)
-\item[2)] We use the fact that \(R\) doesn't constrain the behaviour of \(J_2\):
-	\begin{align*}
-		\sigma_0 \uplus \sigma_{01} \vdash R\mpar{s_0, s_{01}} \iff & \mpar{\bigwedge_{v_1 \in V_1} v_{1'} = v_1}\psubst{\sigma_{01'} \uplus \sigma_{02} \uplus \sigma_{01}} \\
-		\iff & \bigwedge_\subbox{v_1 \in V_1} \sigma_{01'}\mpar{v_{1'}} = \sigma_{01}\mpar{v_1} \\
-		\iff & \top
+\item[2)] We use the fact that \(R\) doesn't constrain the behaviour of \(J_2\) and initial configuration is reachable:
+	\begin{align*}
+		\sigma_0 \uplus \sigma_{01} \vdash R\mpar{s_0, s_{01}} \iff & \mpar{\reach{A}\mpar{s_0} \wedge \bigwedge_{v_1 \in V_1} v_{1'} = v_1}\psubst{\sigma_{01'} \uplus \sigma_{02} \uplus \sigma_{01}} \\
+		\iff & \reach{A}\mpar{s_0}\psubst{\sigma_0} \wedge \bigwedge_\subbox{v_1 \in V_1} \sigma_{01'}\mpar{v_{1'}} = \sigma_{01}\mpar{v_1} \\
+		\iff & \sigma_0 \vdash \reach{A}\mpar{s_0}
 	\end{align*}
@@
 		\iff & \sigma \uplus \nu \vdash \mpar{\reach{A}\mpar{s} \wedge \bigwedge_{v_1 \in V_1} v_{1'} = v_1}\psubst{\psi \uplus \psi_1} \\
-		\iff & \sigma \uplus \nu \vdash \reach{A}\mpar{s}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1} \psi_{1'}\mpar{v_{1'}} = \psi\mpar{v_1} \\
+		\iff & \sigma \uplus \nu \vdash \reach{A}\mpar{s}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1} \psi_{1'}\mpar{v_{1'}} = \psi_1\mpar{v_1} \\
 		\iff & \sigma \uplus \nu \vdash \reach{A}\mpar{s}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1 \cup \fvars{t_1}} v_{1'} = v_1 \\
@@
 	\end{align*}
-\item[\goal{1}:] % TODO: adapt and continue
-	Let \nmm{\sigma: V \uplus V_1 \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
+\item[\goal{1}:] Let \nmm{\sigma: V \uplus V_1 \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
 	We use dummy values for the variables in \nmm{\biguplus_\subbox{t \in \fOT{s}} \fvars{t}} to get the left side of the implication (independant from these values), immediately broken into
@@
 	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{3'} \]
-	We prove \goal{1} with valuation \(\nu\) by admitting the left side ofthe implication and using \hyp{3}.
+	We prove \goal{1} with valuation \(\nu\) by admitting the left side of the implication and using \hyp{3'}.
 \end{proof}
 
-\subsection{Special composition correctness for hole-superset simulation}
+\subsection{Special composition correctness for hole-superset simulation}\label{apx:schs}
 Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and  \(A_3 \defobject \OAg[3]\) be open automata.
@@
 Let \(R_{12}\) be a hole-superset simulation of \(A_1\) by \(A_2\) and \(\reach{A}\) be a witness that \(A\) is non-locking.
-\[ R \defobject \mpar{\mpar{s_1, s_3}, s_2} \mapsto R_{12}\mpar{s_1, s_2} \wedge \reach{A_1\subst{A_3}{k}}\mpar{s_1, s_3} \]
+\[ R \defobject \mpar{\mpar{s_1, s_3}, s_2} \mapsto R_{12}\mpar{s_1, s_2} \wedge \reach{A}\mpar{s_1, s_3} \]
 We want to prove that \(R\) is a hole-superset simulation of \(A\) by \(A_2\).
 \begin{proof}
-\item[1)] % TODO
-\item[2)] % TODO
-\item[3)] % TODO
+\item[1)] \(J = J_3 \cup J_1 \setminus \mbrc{k} \supseteq J_3 \cup J_2 \setminus \mbrc{k} \supseteq J_2 \setminus \mbrc{k} = J_2\)
+\item[2)] We use the fact that \(R_{12}\) relates initial configurations and that initial configuration is reachable:
+	\begin{align*}
+		\sigma_0 \uplus \sigma_{02} \vdash R\mpar{s_0, s_{02}} \iff & \sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03} \vdash R_{12}\mpar{s_{01}, s_{02}} \wedge \reach{A}\mpar{s_0} \\
+		\iff & \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar{\sigma_0 \vdash \reach{A}\mpar{s_0}}
+	\end{align*}
+\item[3)] Let \(s \defobject \mpar{s_1, s_3} \in S\) and \(s_2 \in S_2\).
+	We want to prove both
+	\begin{align*}
+		& \bigsymb{\forall} t \defobject \OTg \in \fOT{s}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
+		& \quad \mpar{\forall x \in X, J'_{2x} \cap J = J' \cap J_2} \\[-10pt]
+		& \nwedge V \uplus V_2 \uplus \fvars{t} \vdash R\mpar{s, s_2} \wedge g \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J} \beta_j = \beta_{2xj} \\[12pt]
+			\nwedge g_{2x} \wedge R\mpar{s', s'_{2x}}\psubst{\psi \uplus \psi_{2x}}
+		\end{array}} \goal{0}
+	\end{align*}
+	\[ V \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \goal{1} \]
+	Let \nmm{t \defobject \OTg \in \fOT{s}}, we use the fact that \(R_{12}\) is a simulation from the states \(\mpar{s_1, s_2}\) to get the hypothesis:
+	\begin{align*}
+		& \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
+		& \quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
+		& \nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R_{12}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
+			\nwedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}} \hyp{1}
+	\end{align*}
+	Transition \(t\) is obtained by composition of \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}} and \nmm{t_3 \defobject \OTx{3}{}{3}{3} \in \fOT{s_3}} if \(k \in J'_1\) or by a the first transition and the state \(s_3\) if \(k \notin J'_1\).
+	We use \hyp{1} with the transition \(t_1\) to get
+	\begin{gather*}
+		\mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X} \\
+		\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2 \hyp{1'} \\
+		V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R_{12}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
+			\nwedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}} \hyp{1"}
+	\end{gather*}
+	We will prove \goal{0} for the family \(t_{2x}\), the new goals are
+	\begin{gather}
+		\forall x \in X, J'_{2x} \cap J = J' \cap J_2 \goal{0'} \\
+		V \uplus V_2 \uplus \fvars{t} \vdash R\mpar{s, s_2} \wedge g \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J} \beta_j = \beta_{2xj} \\[12pt]
+			\nwedge g_{2x} \wedge R\mpar{s', s'_{2x}}\psubst{\psi \uplus \psi_{2x}}
+		\end{array}} \goal{2}
+	\end{gather}
+\item[\goal{0'}:] Let \(x \in X\)
+	\begin{align*}
+		J'_{2x} \cap J & = J'_{2x} \cap \mpar{J_3 \uplus J_1 \setminus \mbrc{k}} \\
+		& = J'_{2x} \cap J_1 & \text{by } k \in J_1 \setminus J_2 \text{ and } \emptyset = J_3 \cap J_1 \supseteq J_3 \cap J_2 \hyp{2} \\
+		& = J'_1 \cap J_2 & \text{by \hyp{1'}} \\
+		& = \mpar{J'_1 \uplus J'_3} \cap J_2 \\
+		& = J' \cap J_2
+	\end{align*}
+\item[\goal{2}:] Let \nmm{\sigma: V \uplus V_2 \uplus \fvars{t} \to \values}.
+	We use dummy values for the variables in \nmm{\biguplus_\subbox{t_{2x} \in \fOT{s_2}} \fvars{t_{2x}}} to get the left side of the implication (independant from these values), immediately broken into
+	\begin{gather}
+		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{3a} \\
+		\sigma \vdash \reach{A}\mpar{s} \hyp{3b} \\
+		\sigma \vdash g \hyp{3c}
+	\end{gather}
+	We use \hyp{1"} with valuation \(\sigma\) on variables \(V_1 \uplus V_2 \uplus \fvars{t_1}\), which is possible because the composition of transitions doesn't remove any variable.
+	Then we get the values of the implicit \(\exists\) in \nmm{\nu: \biguplus_{x \in X} \fvars{t_{2x}}}.
+	The left side of the implication is proved with \hyp{3a} and \hyp{3c}.
+	So we get a \(x \in X\) such that
+	\begin{gather}
+		\sigma \uplus \nu \vdash \alpha_1 = \alpha_{2x} \hyp{4a} \\
+		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \hyp{4b} \\
+		\sigma \uplus \nu \vdash g_{2x} \hyp{4c} \\
+		\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \hyp{4d}
+	\end{gather}
+	In order to progress on \goal{2} we give valuation \(\nu\) for the implicit \(\exists\), admit the left side of the implication and choose to prove the branch \(x\):
+	\begin{gather}
+		\sigma \uplus \nu \vdash \alpha = \alpha_{2x} \goal{2a} \\
+		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_{2x} \cap J} \beta_j = \beta_{2xj} \goal{2b} \\
+		\sigma \uplus \nu \vdash g_{2x} \goal{2c} \\
+		\sigma \uplus \nu \vdash R\mpar{s', s'_{2x}}\psubst{\psi \uplus \psi_{2x}} \goal{2d}
+	\end{gather}
+	\goal{2a} is proved by \hyp{4a} (\(\alpha = \alpha_1\)).
+	\goal{2b} is proved using \hyp{4b} because \(J'_{2x} \cap J = J'_{2x} \cap J_1 = J'_1 \cap J_2\) (\hyp{2} and \hyp{1'}) and \(\forall j \in J'_1, \beta_{1j} = \beta_j\) (transition comes from composition).
+	\goal{2c} is proved by \hyp{4c}.
+	For \goal{2d} we use \hyp{4d} and \hyp{3b} with the preservation of reachability across transitions:
+	\begin{align*}
+		& \sigma \uplus \nu \vdash R\mpar{s', s'_{2x}}\psubst{\psi \uplus \psi_{2x}} \\
+		\iff & \sigma \uplus \nu \vdash \mpar{R_{12}\mpar{s'_1, s'_{2x}} \wedge \reach{A}\mpar{s}}\psubst{\psi_1 \uplus \psi_{2x} \uplus \psi_3} \\
+		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \reach{A}\mpar{s}\psubst{\psi}}
+	\end{align*}
+\item[\goal{1}:] 
+	Let \nmm{\sigma: V \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values}.
+	We use dummy values for the variables in \nmm{\biguplus_\subbox{t \in \fOT{s}} \fvars{t}} to get the left side of the implication (independant from these values), immediately broken into
+	\begin{gather}
+		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{5a} \\
+		\sigma \vdash \reach{A}\mpar{s} \hyp{5b} \\
+		\sigma \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{5c}
+	\end{gather}
+	\(R_{12}\) is a simulation and \(\reach{A}\) is a witness of the non-locking composition so we have the hypotheses:
+	\begin{gather}
+		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6} \\
+		V \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{7}
+	\end{gather}
+	We use \hyp{6} with valuation \(\sigma\) to get \nmm{\nu: \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
+	The left side of the implication is proved with \hyp{5a} and \hyp{5c}, the right side gives the hypothesis:
+	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{6'} \]
+	We then use \hyp{7} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t \in \fOT{s}} \fvars{t}}.
+	The left side of the implication is proved using \hyp{5b} and \hyp{6'}, the right side gives:
+	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{7'} \]
+	We prove \goal{1} with valuation \(\nu'\) by admitting the left side of the implication and using \hyp{7'}.
 \end{proof}
@@
 	\end{align}
-	Finally to prove \goal{2} with valuation \(\nu_3\) for the implicit \(\exists\), we admit the left side of the implication choose to prove the branch \(z\):
+	In order to progress on \goal{2} we give valuation \(\nu_3\) for the implicit \(\exists\), admit the left side of the implication and choose to prove the branch \(z\):
 	\begin{align}
@@
 	\end{gather*}
-	We can use immediately \hyp{8} with state \(s_2\) and valuation \(\sigma_2 \uplus \sigma_3\) to get \nmm{\nu_2: \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values}.
+	We can use \hyp{8} with state \(s_2\) and valuation \(\sigma_2 \uplus \sigma_3\) to get \nmm{\nu_2: \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values}.
 	The left side of the implication is proved with the right side of \hyp{9'} and \hyp{9"}, so we get

### 2021-06-12 2021-Refinement/report.tex
Strategic proof repositionning to spend less time in redundant proofs

@@
 % TODO: CITER LES CONFERENCES
-% TODO: verify cup -> uplus, tell that uplus is disjoint union
 
@@
 However \(\mbrc{\alpha \mapsto 1, \beta \mapsto 2, \gamma \mapsto 3}\) has no generating expression and is represented here with the finite version of first notation.
+
+The disjoint union on set is noted \(\uplus\).
+There are several ways of ensuring a union is disjoint, we will indifferently either suppose sets are disjoint or rename conflicting object (useful for variables).
 The disjoint union of two maps \(\varphi: I \to X\) and \(\psi: J \to Y\) with \(I \cap J = \emptyset\) is \(\varphi \uplus \psi: I \uplus J \to X \cup Y\).
@@
 \begin{defi}[Non-locking composition, intuitive definition]
-Let \(A_c \defobject \OAg[c]\), \(A_p \defobject \OAg[p]\) and \(j \in J_p\).
-The composition \(A \defobject A_p\subst{A_c}{j}\) is non-locking if \(A\) has a reachability predicate satisfying:
-From reachable configurations, if there was a possible transition in \(A_p\) then there is a possible transition in \(A_p\subst{A_c}{j}\).
+Let \(A_i \defobject \OAg[i], 0 \leq i \leq n\).
+The composition \(A \defobject A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is non-locking if \(A\) has a reachability predicate satisfying:
+From reachable configurations, if there was a possible transition in \(A_0\) then there is a possible transition in \(A\).
 
@@
 \begin{multline*}
-	\forall s \defobject \mpar{s_p, s_c} \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A_p\subst{A_c}{j}}\mpar{s}} \implies \\
-	\mpar{\exists t_p \in \fOT{s_p}, \exists \nu_p: \fvars{t_p} \to \values, \sigma \uplus \nu_p \vdash \fguard{t_p}} \implies \\
+	\forall s \defobject \mpar{s_0, s'} \in S_0 \times \prod_\subbox{1 \leq i \leq n} S_i, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A}\mpar{s}} \implies \\
+	\mpar{\exists t_0 \in \fOT{s_0}, \exists \nu_0: \fvars{t_0} \to \values, \sigma \uplus \nu_0 \vdash \fguard{t_0}} \implies \\
 	\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t}
@@
 \end{defi}
-We can expand the aliases \(S, V\) into \(S_p \times S_c, V_p \uplus V_c\) and transform the last transition \(t\) into a pair \(\mpar{t_p, t}\) where the first transition is the one from \(A_p\) which generated \(t\).
+We can expand the alias \(V\) into \nmm{\biguplus_\subbox{1 \leq i \leq n} V_i \uplus V_0} and transform the last transition \(t\) into a pair \(\mpar{t, t_0}\) where the second transition is the one from \(A_0\) which generated \(t\).
 Doing that makes the definition become mildly similar with the deadlock prevention one. % OR slightly
@@
 \begin{defi}[Non-locking composition, working definition]
-The composition \(A \defobject A_p\subst{A_c}{j}\) is a non-locking composition if:
-\[ \forall s \defobject \mpar{s_p, s_c} \in S, V \uplus \biguplus_\subbox{t_p \in \fOT{s_p}} \fvars{t_p} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
+\(A \defobject A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is a non-locking composition if:
+\[ \forall s \defobject \mpar{s_0, s'} \in S, V \uplus \biguplus_\subbox{t_0 \in \fOT{s_0}} \fvars{t_0} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_0 \in \fOT{s_0}} \fguard{t_0} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
 \end{defi}
@@
 
-This new definition of composition can replace the standard composition in the case where only one hole is filled, and also be extended to a simultaneous composition.
-For the simultaneous composition, we may think that if the last composition of a specific composition order is non-locking, then every composition is non-locking for all composition order. % orderS
+This new definition of composition can replace the standard composition.
+For the simultaneous composition, we may think that if the last composition of a specific composition order is non-locking, then every composition is non-locking for all composition orders.
 Unfortunately it is not true.
@@
 \(R\) is a witness of the transitivity, proof is given in Appendix \ref{apx:trans}.
-\begin{thm}[Context refinement] Hole-equal simulation is context refining. \end{thm}
-Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) with \(J_1 = J_2\).
-Let \(k \in J_1\), \(R_{12}\) be a hole-equal simulation of \(A_1\) by \(A_2\) and \(\reach{A\subst{A_3}{k}}\) be a witness that \(A\subst{A_3}{k}\) is non-locking.
-The idea for the relation on configurations is that \(A_2\) simulates \(A_1\) while \(A_3\) does the same things in both compositions in the hole \(k\).
-\[ R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \]
-Where \(y_{3x}\) is the renaming of \(y_3\) from \(A_3\) in \(A_x\subst{A_3}{k}\).
-\(R\) is a witness of the context refinement, proof is given in Appendix \ref{apx:crhe}.
 \begin{prop}[Limited composition correctness]\label{prop:cc'} Hole-subset simulation is correct w.r.t.\@ composition with automata without holes. \end{prop}
@@
 
-% TODO HERE
-% J'2 \subseteq J'1 in hole-subset, J'1 \subseteq J'2 in hole-superset (decide of transition variable with holes); composition with new holes is hole-subset where hole variables are free then hole-superset where hole names have no conflicts with removed holes.
-Transitivity must ensure holes name have no conflict for that reason!
-
-% Explain what happens on holes constraints and action constraints
-% refinement can be used to specify behaviour/constraints on holes (like an API: first do anything not involving the api, then initialise the api, then do whatever you want that do not unload the api, then unload the api by returning to the first state), then have a relation for every hole with a different automata and this means well behaving with respect to the environement (holes)
+For composition correctness, the hole-subset simulation can only tell if there is a refinement when the composed automata have no holes.
+To lift this limitation we need to allow adding holes which doesn't have a direct interpretation.
+At first a solution using a function mapping the action performed by the new holes in the composition to the ones performed by removed hole in the base automaton was explored.
+It was abandonned because the base automaton has nothing intelligent to tell about the action required by the composed automata.
+That is the reason the hole-superset simulation doesn't constrain the action performed by the added holes.
+
+Only one of the hole-\(\triangle\) simulations cannot tell that a non-locking composition with any automaton is a refinement because we need at the same time to add and remove holes, hence the need of the special composition correctness for hole-superset.
+ALso an issue arises when trying to tell that a composition is a refinement of the base automaton: the refinement relation cannot compare the holes sets.
+This conflicts with the transitivity propriety when a hole present in both extrema of the chain is absent in an intermediate automaton.
+In that case all the constraint on holes actions are lifted even if we would like to require an equality of these actions on the transitive cloture.
+
 \section{Refinement relation for open automata}\label{sec:refinement}
-% TODO: intro
+One of the solutions to keep transitivity and constraints on holes actions from same holes is to keep track of which holes are in common at each step of refinement.
+The transitive refinement will have to either rename the holes without constraints or explicitly say which holes have constraints.
 \begin{defi}[Open automata refinement]
@@
 \end{multline*}
-\end{defi}
-% refinement relation definition
-% Explain definition, really needed
-% safety is no longer trivial, prove the safety
-% Prove all expected properties except pre-simulation
-
-% What happens on untracked holes (untracked holes equivalent behaviour => free variables; some sort of daisy equivalence)
-% Yet having untracked holes is interesting because we can be a refinement of several OA, each on different holes.
-
-\section{Future work}
-% TODO: Weak variants, tau-stuttering, livelocks
-% Other kind of refinement relation that \Quentin{I may explore}{This is a note for possible path, some may be explored, some may not.} are control refinement/hole refinement\footnote{No good formulation atm, the idea is that \(a \leq b \defnotation sth \wedge J_a \setminus J_b \leq_{ctrl} J_b \setminus J_a\), sth is probably a clause to ensure that they behave the same without holes involved.}, (meet semi)lattice refinement\footnote{meet = handshake, \(a \leq b \defnotation a = a || b\) with sync holes, I think this will be equivalent to hole-identical sim, (join=non-det choice?)}, weak-simulation refinement\footnote{Weak variation for each interesting simulation refinement}, composition-correct refinement\footnote{Basically a stricter variant of simulation-refinement where simulation has to take place the other way for some transitions (no different holes?) in order to be correct wrt composition}.
+Giving \(R\) and \(H\) is sufficient to characterise the refinement, so we call \(\mpar{R, H}\) a hole-tracking simulation of \(A_1\) by \(A_2\).
+\end{defi}
+It is basically the same definition as the refinement relation deduced from hole-\(\triangle\) simulations.
+\(R\) is a kind of hole-\(\triangle\) simulation but without the \(\triangle\) constraint on hole sets.
+On top of that every actions of the holes outside \(H\) is unconstrained in the related automata.
+
+The transitivity property becomes \(\wrel{X}{A}{B} \wedge \wrel{Y}{B}{C} \implies \wrel{X \cap Y}{A}{C}\).
+It behaves the same as if the holes outside the intersection were renamed to avoid conflicts in the first place.
+This makes the comination of the transitivity proofs of hole-\(\triangle\) simulation sufficient to prove transitivity.
+
+Not renaming conflicting holes still have an interest.
+If we are trying to build an automaton \(A\) with several constraints \(A \leq B_i, i \in I\) -method B like- and each \(B_i\) is a refinement of some automaton \(C\) then we can have each \(B_i\) constrain a different subset of \(A\)'s holes.
+On each individual path \(A \leq B_i \leq C\), some holes of \(A\) are unconstrained but when considering all path they are all constrained.
+
+The other interesting properties left to check are correctness w.r.t.\@ composition, context refinement, composition congruence and compatibility with FH-bisimulation.
+Proving them for the open automata refinement will also prove them for each hole-\(\triangle\) simulation as they are just restricted cases.
+% TODO: Explain two refinement steps comositions so that Correctness wrt composition is trivial
+\begin{thm}[Context refinement] Open automata refinement is context refining. \end{thm}
+Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\).
+Let \(k \in J_1 \cap J_2\), \(\mpar{R_{12}, H_{12}}\) be a hole-tracking simulation of \(A_1\) by \(A_2\) and \(\reach{A\subst{A_3}{k}}\) be a witness that \(A\subst{A_3}{k}\) is non-locking.
+The idea for the relation on configurations is that \(A_2\) simulates \(A_1\) while \(A_3\) does the same things in both compositions in the hole \(k\).
+\begin{gather*}
+	R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \\
+	H \defobject J_3 \uplus H_{12} \setminus \mbrc{k}
+\end{gather*}
+Where \(y_{3x}\) is the renaming of \(y_3\) from \(A_3\) in \(A_x\subst{A_3}{k}\).
+\(\mpar{R, H}\) is a witness of \(\wrel{H}{A_{13}}{A_{23}}\), proof is given in Appendix \ref{apx:cr}.
+% TODO: Proof for Congruence \ref{apx:cong}
+% TODO: Proof for FH-bisimulation compatibility \ref{apx:FHbcomp}
+
+% TODO: What happens on untracked holes (untracked holes equivalent behaviour => free variables; some sort of daisy equivalence)
 
 \section{Conclusion}
+% TODO: recap contribs?
+
+The refinement presented here still do not work on the motivating example because of silent actions.
+To be able to refine in the presence of silent action, a weak variant of the simulation is needed.
+This variant will also probably be able to encompass action refinement as a valid refinement because the mechanism are similar.
 
@@
 
-\subsection{Context refinement for hole-equal simulation}\label{apx:crhe}
-Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) be three open automata.
-Let \(k \in J_1\), \(A_{13} \defobject A_1\subst{A_3}{k}\) and \(A_{23} \defobject A_2\subst{A_3}{k}\).
-Let \(R_{12}\) be a hole-equal simulation of \(A_1\) by \(A_2\) and \(\reach{A_{13}}\) be a witness that \(A_{13}\) is non-locking.
-We pose \(A_{13} = \OAg[13]\) and \(A_{23} = \OAg[23]\).
-\[ R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \]
-Where \(y_{3x}\) is the renaming of \(y_3\) from \(A_3\) in \(A_{x3}\).
-We want to prove that \(R\) is a hole-equal simulation of \(A_{12}\) by \(A_{23}\).
-\begin{proof}
-\item[1)] \(J_{13} = J_3 \cup J_1 \setminus \mbrc{k} = J_3 \cup J_2 \setminus \mbrc{k} = J_{23}\) by \(J_1 = J_2\).
-\item[2)] For \(\sigma_{013} \uplus \sigma_{023} \vdash R\mpar{s_{013}, s_{023}}\) we use the fact that \(R_{12}\) relates inital configurations and initial configuration is reachable:
-	\begin{align*}
-		& \sigma_{013} \uplus \sigma_{023} \vdash R\mpar{s_{013}, s_{023}} \\
-		\iff & R\mpar{\mpar{s_{01}, s_{031}}, \mpar{s_{02}, s_{031}}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{031} \uplus \sigma_{032}} \\
-		\iff & R_{12}\mpar{s_{01}, s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}\psubst{\sigma_{013}} \wedge \mpar{\bigwedge_{v_3 \in V_3} v_{31} = v_{32}}\psubst{\sigma_{031} \uplus \sigma_{032}} \\
-		\iff & \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}} \wedge \bigwedge_\subbox{v_3 \in V_3} \sigma_{031}\mpar{v_{31}} = \sigma_{032}\mpar{v_{32}} \\
-		\iff & \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}} \wedge \top
-	\end{align*}
-\item[3)] Let \(s_{13} \defobject \mpar{s_1, s_{31}} \in S_{13}\) and \(s_{23} \defobject \mpar{s_2, s_{32}} \in S_{23}\).
-	We want to prove both
-	\begin{align*}
-		& \bigsymb{\forall} t_{13} \defobject \OTx{13}{}{13}{13} \in \fOT{s_{13}}, \bigsymb{\exists} \mpar{t_{23x} \defobject \OTx{23}{x}{23x}{23x} \in \fOT{s_{23}}}^{x \in X}, \\
-		& \quad \mpar{\forall x \in X, J'_{23x} \cap J_{13} = J'_{13} \cap J_{23}} \\[-10pt]
-		& \nwedge V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \Rightarrow \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\!\!\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \\[12pt]
-			\nwedge g_{23x} \wedge R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
-		\end{array}\!\!} \goal{0}
-	\end{align*}
-	\[ V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash R\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \goal{1} \]
-	Let \nmm{t_{13} \defobject \OTx{13}{}{13}{13} \in \fOT{s_{13}}}, we use the fact that \(R_{12}\) is a simulation from the states \(\mpar{s_1, s_2}\) to get the hypothesis:
-	\begin{align*}
-		& \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
-		& \quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
-		& \nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}} \hyp{1}
-	\end{align*}
-	Transition \(t_{13}\) is obtained in \(A_{13}\) by composition of two transitions \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}} and \nmm{t_{31} \defobject \OTx{31}{}{31}{31} \in \fOT{s_{31}}} if \(k \in J'_1\) or by a the first transition and the state \(s_{31}\) if \(k \notin J'_1\).
-	We use \hyp{1} with the transition \(t_1\) to get
-	\begin{gather*}
-		\mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X} \\
-		\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2 \hyp{1'} \\
-		V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}} \hyp{1"}
-	\end{gather*}
-	To build the family of transitions we need to know if \(k \in J'_{2x}\) for a every \(x \in X\):
-	\begin{align*}
-		J'_1 & = J'_1 \cap J_1 \\
-		& = J'_1 \cap J_2 & \text{by } J_1 = J_2 \\
-		& = J'_{2x} \cap J_1 & \text{by \hyp{1'}} \\
-		& = J'_{2x} \cap J_2 & \text{by } J_1 = J_2 \\
-		& = J'_{2x} \hyp{2}
-	\end{align*}
-	In the case \(s_{31} \neq s_{32}\) we can give the empty family, it won't cause any issue.
-	Otherwise \(s_{31} = s_{32}\) so we can copy \(t_{31}\) into \nmm{t_{32} = \OTx{32}{}{32}{32}} to avoid conflicts.
-	We also name \(t_3\) the original transition from \(T_3\).
-	Using \hyp{2} we can build the familly of transition generated by the family \(t_{2x}^{x \in X}\):
-	\[ t_{23x}^{x \in X} \defobject x \mapsto \choice{
-		\OT{\mpar{s_2, s_{32}}}{\mpar{s'_{2x}, s'_{32}}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x} \setminus \mbrc{k}} \uplus \beta_{3j}^{j \in J'_{32}}}{g_{2x} \wedge g_{32} \wedge \alpha_{32} = \beta_{2xk}}{\psi_{2x} \uplus \psi_{32}} & \text{if } k \in J'_{2x} \\
-		\OT{\mpar{s_2, s_{32}}}{\mpar{s'_{2x}, s_{32}}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_2}}{g_2}{\psi_2} & \text{otherwise}
-	} \]
-	We will prove \goal{0} for the family \(t_{23x}^{x \in X}\), the new goals are
-	\begin{gather}
-		\forall x \in X, J'_{23x} \cap J_{13} = J'_{13} \cap J_{23} \goal{0'} \\
-		V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \\[12pt]
-			\nwedge g_{23x} \wedge R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
-		\end{array}} \goal{2}
-	\end{gather}
-\item[\goal{0'}:] Let \(x \in X\), by case on \(k \in J'_1\):
-	\begin{align*}
-		\text{If } k \in J'_1: && J'_{23x} \cap J_{13} & = \mpar{J'_{31} \cup J'_{2x} \setminus \mbrc{k}} \cap \mpar{J_3 \cup J_1 \setminus \mbrc{k}} \\
-		&&& = \mpar{J'_{31} \cap J_3} \cup \mpar{J'_{2x} \cap J_1} \setminus \mbrc{k} \\
-		&&& = \mpar{J'_{31} \cap J_3} \cup \mpar{J'_1 \cap J_2} \setminus \mbrc{k} & \text{by \hyp{1'}} \\
-		&&& = \mpar{J'_{31} \cup J'_1 \setminus \mbrc{k}} \cap \mpar{J_3 \cup J_2 \setminus \mbrc{k}} \\
-		&&& = J'_{13} \cap J_{23} \\
-		\text{If } k \notin J'_1: && J'_{23x} \cap J_{13} & = \mpar{J'_{2x} \setminus \mbrc{k}} \cap \mpar{J_1 \setminus \mbrc{k}} \\
-		&&& = J'_{2x} \cap J_1 & \text{by } k \notin J'_1 = J'_{2x} \text{ \hyp{2}} \\
-		&&& = J'_1 \cap J_2 & \text{by \hyp{1'}} \\
-		&&& = \mpar{J'_1 \setminus \mbrc{k}} \cap \mpar{J_2 \setminus \mbrc{k}} & \text{by } k \notin J'_1 \\
-		&&& = J'_{13} \cap J_{23}
-	\end{align*}
-\item[\goal{2}:] Let \(\sigma: V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \to \values\).
-	We use dummy values for the variables in \nmm{\biguplus_{x \in X} \fvars{t_{23x}}} to get the left side of the implication as an hypothesis (independant from these values):
-	\[ \sigma \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \hyp{3} \]
-	If \(s_{31} \neq s_{32}\) then this hypothesis is \(\sigma \vdash \bot\), the empty family works and the proof is finished.
-	We can assume \(s_{31} = s_{32}\) and break \hyp{3} into
-	\begin{gather}
-		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{3a} \\
-		\sigma \vdash \reach{A_{13}}\mpar{s_{13}} \hyp{3b} \\
-		\sigma \vdash \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} \hyp{3c} \\
-		\sigma \vdash g_{13} \hyp{3d}
-	\end{gather}
-	We use \hyp{1"} with valuation \(\sigma\) on variables \(V_1 \uplus V_2 \uplus \fvars{t_1}\), which is possible because the composition of transitions doesn't remove any variable (the simplification steps do, they give bisimilar automata).
-	Then we get the values of the implicit \(\exists\) in \nmm{\nu: \biguplus_{x \in X} \fvars{t_{2x}}}.
-	The left side of the implication is proved with \hyp{3a} and \hyp{3d}.
-	So we get a \(x \in X\) such that
-	\begin{gather}
-		\sigma \uplus \nu \vdash \alpha_1 = \alpha_{2x} \hyp{4a} \\
-		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \hyp{4b} \\
-		\sigma \uplus \nu \vdash g_{2x} \hyp{4c} \\
-		\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \hyp{4d}
-	\end{gather}
-	If \(k \in J'_1\), we extend the valuation \(\nu\) to cover the variables of \(t_3\) in \(t_{23x}\) using their value in \(t_{13}\), \(\nu' \defobject \nu \uplus \mset{v_{32} \mapsto \sigma\mpar{v_{31}}}{v_3 \in \fvars{t_3}}\)
-	Otherwise \(\nu' \defobject \nu\).
-	We progress on \goal{2} by giving the valuation \(\sigma \uplus \nu'\) to the implicit \(\exists\), admitting the left side of the implication and choosing to prove the branch \(x\) of the disjunction:
-	\begin{gather}
-		\sigma \uplus \nu' \vdash \alpha_{13} = \alpha_{23x} \goal{3a} \\
-		\sigma \uplus \nu' \vdash \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \goal{3b} \\
-		\sigma \uplus \nu' \vdash g_{23x} \goal{3c} \\
-		\sigma \uplus \nu' \vdash R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}} \goal{3d}
-	\end{gather}
-	Because composition doesn't change the produced actions nor its variables, \goal{3a} is proved by \hyp{4a}.
-	\goal{3b} holds because the valuations for the actions of the holes in \(J_3\) coincide by definition of \(\nu'\) and by \hyp{4b} for the others.
-	For \goal{3c} we have two cases, if \(k \notin J'_1\) then \(g_{23x} \equiv g_{2x}\) and \hyp{4c} is sufficient, if \(k \in J'_1\) then \(g_{23x} \equiv g_{2x} \wedge g_3 \wedge \alpha_3 = \beta_{2xk}\) so we also need \hyp{3d} (\(g_{13} \equiv g_1 \wedge g_3 \wedge \alpha_3 = \beta_{1k}\)) and \hyp{4b} for the value \(k\) (\(\beta_{1k} = \beta_{2xk}\)).
-	\goal{3d} is proved using \hyp{4d}, \hyp{3b} with the preservation of reachability across transitions (+ \hyp{3d}), \hyp{3c} and the fact that \(A_3\) performs the same transition with same values in both composed automata:
-	\begin{align*}
-		& \sigma \uplus \nu' \vdash R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}} \\
-		\iff & \sigma \uplus \nu' \vdash \mpar{R_{12}\mpar{s'_1, s'_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32}}\psubst{\psi_1 \uplus \psi_{31} \uplus \psi_{2x} \uplus \psi_{32}} \\
-		\iff & \sigma \uplus \nu' \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}} \wedge \bigwedge_\subbox{v_3 \in V_3} \psi_{31}\mpar{v_{31}} = \psi_{32}\mpar{v_{32}} \\
-		\iff & \sigma \uplus \nu' \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}} \wedge \bigwedge_\subbox{v_3 \in V_3 \cup \fvars{t_3}} v_{31} = v_{32} \\
-		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}}} \wedge \mpar{\sigma \vdash \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32}}
-	\end{align*}
-\item[\goal{1}:] Let \nmm{\sigma: V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \to \values}.
-	We use dummy values for the variables in \nmm{\biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}}} to get the left side of the implication (independant from these values), immediately broken into
-	\begin{gather}
-		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{5a} \\
-		\sigma \vdash \reach{A_{13}}\mpar{s_{13}} \hyp{5b} \\
-		\sigma \vdash \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \hyp{5c}
-	\end{gather}
-	\(R_{12}\) is a simulation and \(\reach{A_{13}}\) is a witness of the non-locking composition so we have the hypotheses:
-	\begin{gather}
-		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6} \\
-		V_{13} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{7}
-	\end{gather}
-	We use \hyp{6} with valuation \(\sigma\) projected on the variables from generating transitions in \(A_2\) to get \nmm{\nu: \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
-	The left side of the implication is proved using \hyp{5a} and \hyp{5c} because the guards from transitions of \(A_2\) are still in transitions of \(A_{23}\), the right side gives:
-	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6'} \]
-	We then use \hyp{7} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}}}.
-	The left side of the implication is proved using \hyp{5b} and \hyp{6'}, the right side gives:
-	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{7'} \]
-	\goal{1} is proved for valuation \(\nu'\) by admitting the left side and using \hyp{7'}.
-\end{proof}
-
 \subsection{Limited composition correctness for hole-subset simulation}\label{apx:lchs}
@@
 \begin{proof}
-\item[1)] \(J = J_2 \cup J_1 \setminus \mbrc{k} = \emptyset \cup J_1 \setminus \mbrc{k} \subseteq J_1\)
+\item[1)] \(J = J_2 \uplus J_1 \setminus \mbrc{k} = \emptyset \uplus J_1 \setminus \mbrc{k} \subseteq J_1\)
 \item[2)] We use the fact that \(R\) doesn't constrain the behaviour of \(J_2\) and initial configuration is reachable:
@@
 \item[\goal{0'}:] \(t\) is a transition built from \(t_1\) so it has its holes.
-	Additionnally either \(k \notin J'_1\) so \(J' = J'_1\) or \(k \in J'_1\) so \(J' = \emptyset \cup J'_1 \setminus \mbrc{k}\) because \(A_2\) has no holes.
+	Additionnally either \(k \notin J'_1\) so \(J' = J'_1\) or \(k \in J'_1\) so \(J' = \emptyset \uplus J'_1 \setminus \mbrc{k}\) because \(A_2\) has no holes.
 	Either case \(J'_1 \cap J = J'_1 \setminus \mbrc{k} = \mpar{J'_1 \setminus \mbrc{k}} \cap J_1 = J' \cap J_1\).
@@
 		\iff & \sigma \uplus \nu \vdash \reach{A}\mpar{s}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1} \psi_{1'}\mpar{v_{1'}} = \psi_1\mpar{v_1} \\
-		\iff & \sigma \uplus \nu \vdash \reach{A}\mpar{s}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1 \cup \fvars{t_1}} v_{1'} = v_1 \\
+		\iff & \sigma \uplus \nu \vdash \reach{A}\mpar{s}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1 \uplus \fvars{t_1}} v_{1'} = v_1 \\
 		\iff & \mpar{\sigma \vdash \reach{A}\mpar{s}\psubst{\psi}} \wedge \mpar{\sigma \uplus \nu \vdash \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1}
@@
 \begin{proof}
-\item[1)] \(J = J_3 \cup J_1 \setminus \mbrc{k} \supseteq J_3 \cup J_2 \setminus \mbrc{k} \supseteq J_2 \setminus \mbrc{k} = J_2\)
+\item[1)] \(J = J_3 \uplus J_1 \setminus \mbrc{k} \supseteq J_3 \uplus J_2 \setminus \mbrc{k} \supseteq J_2 \setminus \mbrc{k} = J_2\)
 \item[2)] We use the fact that \(R_{12}\) relates initial configurations and that initial configuration is reachable:
@@
 
+\section{Proof or properties for open automata refinement}
+
+\subsection{Context refinement}\label{apx:cr} % TODO HERE: adapt
+Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) be three open automata.
+Let \(k \in J_1\), \(A_{13} \defobject A_1\subst{A_3}{k}\) and \(A_{23} \defobject A_2\subst{A_3}{k}\).
+Let \(R_{12}\) be a hole-equal simulation of \(A_1\) by \(A_2\) and \(\reach{A_{13}}\) be a witness that \(A_{13}\) is non-locking.
+We pose \(A_{13} = \OAg[13]\) and \(A_{23} = \OAg[23]\).
+\[ R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \]
+Where \(y_{3x}\) is the renaming of \(y_3\) from \(A_3\) in \(A_{x3}\).
+We want to prove that \(R\) is a hole-equal simulation of \(A_{12}\) by \(A_{23}\).
+\begin{proof}
+\item[1)] \(J_{13} = J_3 \uplus J_1 \setminus \mbrc{k} = J_3 \uplus J_2 \setminus \mbrc{k} = J_{23}\) by \(J_1 = J_2\).
+\item[2)] For \(\sigma_{013} \uplus \sigma_{023} \vdash R\mpar{s_{013}, s_{023}}\) we use the fact that \(R_{12}\) relates inital configurations and initial configuration is reachable:
+	\begin{align*}
+		& \sigma_{013} \uplus \sigma_{023} \vdash R\mpar{s_{013}, s_{023}} \\
+		\iff & R\mpar{\mpar{s_{01}, s_{031}}, \mpar{s_{02}, s_{031}}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{031} \uplus \sigma_{032}} \\
+		\iff & R_{12}\mpar{s_{01}, s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}\psubst{\sigma_{013}} \wedge \mpar{\bigwedge_{v_3 \in V_3} v_{31} = v_{32}}\psubst{\sigma_{031} \uplus \sigma_{032}} \\
+		\iff & \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}} \wedge \bigwedge_\subbox{v_3 \in V_3} \sigma_{031}\mpar{v_{31}} = \sigma_{032}\mpar{v_{32}} \\
+		\iff & \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}} \wedge \top
+	\end{align*}
+\item[3)] Let \(s_{13} \defobject \mpar{s_1, s_{31}} \in S_{13}\) and \(s_{23} \defobject \mpar{s_2, s_{32}} \in S_{23}\).
+	We want to prove both
+	\begin{align*}
+		& \bigsymb{\forall} t_{13} \defobject \OTx{13}{}{13}{13} \in \fOT{s_{13}}, \bigsymb{\exists} \mpar{t_{23x} \defobject \OTx{23}{x}{23x}{23x} \in \fOT{s_{23}}}^{x \in X}, \\
+		& \quad \mpar{\forall x \in X, J'_{23x} \cap J_{13} = J'_{13} \cap J_{23}} \\[-10pt]
+		& \nwedge V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \Rightarrow \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\!\!\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \\[12pt]
+			\nwedge g_{23x} \wedge R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
+		\end{array}\!\!} \goal{0}
+	\end{align*}
+	\[ V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash R\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \goal{1} \]
+	Let \nmm{t_{13} \defobject \OTx{13}{}{13}{13} \in \fOT{s_{13}}}, we use the fact that \(R_{12}\) is a simulation from the states \(\mpar{s_1, s_2}\) to get the hypothesis:
+	\begin{align*}
+		& \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
+		& \quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
+		& \nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
+			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}} \hyp{1}
+	\end{align*}
+	Transition \(t_{13}\) is obtained in \(A_{13}\) by composition of two transitions \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}} and \nmm{t_{31} \defobject \OTx{31}{}{31}{31} \in \fOT{s_{31}}} if \(k \in J'_1\) or by a the first transition and the state \(s_{31}\) if \(k \notin J'_1\).
+	We use \hyp{1} with the transition \(t_1\) to get
+	\begin{gather*}
+		\mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X} \\
+		\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2 \hyp{1'} \\
+		V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
+			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}} \hyp{1"}
+	\end{gather*}
+	To build the family of transitions we need to know if \(k \in J'_{2x}\) for a every \(x \in X\):
+	\begin{align*}
+		J'_1 & = J'_1 \cap J_1 \\
+		& = J'_1 \cap J_2 & \text{by } J_1 = J_2 \\
+		& = J'_{2x} \cap J_1 & \text{by \hyp{1'}} \\
+		& = J'_{2x} \cap J_2 & \text{by } J_1 = J_2 \\
+		& = J'_{2x} \hyp{2}
+	\end{align*}
+	In the case \(s_{31} \neq s_{32}\) we can give the empty family, it won't cause any issue.
+	Otherwise \(s_{31} = s_{32}\) so we can copy \(t_{31}\) into \nmm{t_{32} = \OTx{32}{}{32}{32}} to avoid conflicts.
+	We also name \(t_3\) the original transition from \(T_3\).
+	Using \hyp{2} we can build the familly of transition generated by the family \(t_{2x}^{x \in X}\):
+	\[ t_{23x}^{x \in X} \defobject x \mapsto \choice{
+		\OT{\mpar{s_2, s_{32}}}{\mpar{s'_{2x}, s'_{32}}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x} \setminus \mbrc{k}} \uplus \beta_{3j}^{j \in J'_{32}}}{g_{2x} \wedge g_{32} \wedge \alpha_{32} = \beta_{2xk}}{\psi_{2x} \uplus \psi_{32}} & \text{if } k \in J'_{2x} \\
+		\OT{\mpar{s_2, s_{32}}}{\mpar{s'_{2x}, s_{32}}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_2}}{g_2}{\psi_2} & \text{otherwise}
+	} \]
+	We will prove \goal{0} for the family \(t_{23x}^{x \in X}\), the new goals are
+	\begin{gather}
+		\forall x \in X, J'_{23x} \cap J_{13} = J'_{13} \cap J_{23} \goal{0'} \\
+		V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \\[12pt]
+			\nwedge g_{23x} \wedge R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
+		\end{array}} \goal{2}
+	\end{gather}
+\item[\goal{0'}:] Let \(x \in X\), by case on \(k \in J'_1\):
+	\begin{align*}
+		\text{If } k \in J'_1: && J'_{23x} \cap J_{13} & = \mpar{J'_{31} \uplus J'_{2x} \setminus \mbrc{k}} \cap \mpar{J_3 \uplus J_1 \setminus \mbrc{k}} \\
+		&&& = \mpar{J'_{31} \cap J_3} \uplus \mpar{J'_{2x} \cap J_1} \setminus \mbrc{k} \\
+		&&& = \mpar{J'_{31} \cap J_3} \uplus \mpar{J'_1 \cap J_2} \setminus \mbrc{k} & \text{by \hyp{1'}} \\
+		&&& = \mpar{J'_{31} \uplus J'_1 \setminus \mbrc{k}} \cap \mpar{J_3 \uplus J_2 \setminus \mbrc{k}} \\
+		&&& = J'_{13} \cap J_{23} \\
+		\text{If } k \notin J'_1: && J'_{23x} \cap J_{13} & = \mpar{J'_{2x} \setminus \mbrc{k}} \cap \mpar{J_1 \setminus \mbrc{k}} \\
+		&&& = J'_{2x} \cap J_1 & \text{by } k \notin J'_1 = J'_{2x} \text{ \hyp{2}} \\
+		&&& = J'_1 \cap J_2 & \text{by \hyp{1'}} \\
+		&&& = \mpar{J'_1 \setminus \mbrc{k}} \cap \mpar{J_2 \setminus \mbrc{k}} & \text{by } k \notin J'_1 \\
+		&&& = J'_{13} \cap J_{23}
+	\end{align*}
+\item[\goal{2}:] Let \(\sigma: V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \to \values\).
+	We use dummy values for the variables in \nmm{\biguplus_{x \in X} \fvars{t_{23x}}} to get the left side of the implication as an hypothesis (independant from these values):
+	\[ \sigma \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \hyp{3} \]
+	If \(s_{31} \neq s_{32}\) then this hypothesis is \(\sigma \vdash \bot\), the empty family works and the proof is finished.
+	We can assume \(s_{31} = s_{32}\) and break \hyp{3} into
+	\begin{gather}
+		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{3a} \\
+		\sigma \vdash \reach{A_{13}}\mpar{s_{13}} \hyp{3b} \\
+		\sigma \vdash \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} \hyp{3c} \\
+		\sigma \vdash g_{13} \hyp{3d}
+	\end{gather}
+	We use \hyp{1"} with valuation \(\sigma\) on variables \(V_1 \uplus V_2 \uplus \fvars{t_1}\), which is possible because the composition of transitions doesn't remove any variable (the simplification steps do, they give bisimilar automata).
+	Then we get the values of the implicit \(\exists\) in \nmm{\nu: \biguplus_{x \in X} \fvars{t_{2x}}}.
+	The left side of the implication is proved with \hyp{3a} and \hyp{3d}.
+	So we get a \(x \in X\) such that
+	\begin{gather}
+		\sigma \uplus \nu \vdash \alpha_1 = \alpha_{2x} \hyp{4a} \\
+		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \hyp{4b} \\
+		\sigma \uplus \nu \vdash g_{2x} \hyp{4c} \\
+		\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \hyp{4d}
+	\end{gather}
+	If \(k \in J'_1\), we extend the valuation \(\nu\) to cover the variables of \(t_3\) in \(t_{23x}\) using their value in \(t_{13}\), \(\nu' \defobject \nu \uplus \mset{v_{32} \mapsto \sigma\mpar{v_{31}}}{v_3 \in \fvars{t_3}}\)
+	Otherwise \(\nu' \defobject \nu\).
+	We progress on \goal{2} by giving the valuation \(\sigma \uplus \nu'\) to the implicit \(\exists\), admitting the left side of the implication and choosing to prove the branch \(x\) of the disjunction:
+	\begin{gather}
+		\sigma \uplus \nu' \vdash \alpha_{13} = \alpha_{23x} \goal{3a} \\
+		\sigma \uplus \nu' \vdash \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \goal{3b} \\
+		\sigma \uplus \nu' \vdash g_{23x} \goal{3c} \\
+		\sigma \uplus \nu' \vdash R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}} \goal{3d}
+	\end{gather}
+	Because composition doesn't change the produced actions nor its variables, \goal{3a} is proved by \hyp{4a}.
+	\goal{3b} holds because the valuations for the actions of the holes in \(J_3\) coincide by definition of \(\nu'\) and by \hyp{4b} for the others.
+	For \goal{3c} we have two cases, if \(k \notin J'_1\) then \(g_{23x} \equiv g_{2x}\) and \hyp{4c} is sufficient, if \(k \in J'_1\) then \(g_{23x} \equiv g_{2x} \wedge g_3 \wedge \alpha_3 = \beta_{2xk}\) so we also need \hyp{3d} (\(g_{13} \equiv g_1 \wedge g_3 \wedge \alpha_3 = \beta_{1k}\)) and \hyp{4b} for the value \(k\) (\(\beta_{1k} = \beta_{2xk}\)).
+	\goal{3d} is proved using \hyp{4d}, \hyp{3b} with the preservation of reachability across transitions (+ \hyp{3d}), \hyp{3c} and the fact that \(A_3\) performs the same transition with same values in both composed automata:
+	\begin{align*}
+		& \sigma \uplus \nu' \vdash R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}} \\
+		\iff & \sigma \uplus \nu' \vdash \mpar{R_{12}\mpar{s'_1, s'_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32}}\psubst{\psi_1 \uplus \psi_{31} \uplus \psi_{2x} \uplus \psi_{32}} \\
+		\iff & \sigma \uplus \nu' \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}} \wedge \bigwedge_\subbox{v_3 \in V_3} \psi_{31}\mpar{v_{31}} = \psi_{32}\mpar{v_{32}} \\
+		\iff & \sigma \uplus \nu' \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}} \wedge \bigwedge_\subbox{v_3 \in V_3 \uplus \fvars{t_3}} v_{31} = v_{32} \\
+		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}}} \wedge \mpar{\sigma \vdash \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32}}
+	\end{align*}
+\item[\goal{1}:] Let \nmm{\sigma: V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \to \values}.
+	We use dummy values for the variables in \nmm{\biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}}} to get the left side of the implication (independant from these values), immediately broken into
+	\begin{gather}
+		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{5a} \\
+		\sigma \vdash \reach{A_{13}}\mpar{s_{13}} \hyp{5b} \\
+		\sigma \vdash \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \hyp{5c}
+	\end{gather}
+	\(R_{12}\) is a simulation and \(\reach{A_{13}}\) is a witness of the non-locking composition so we have the hypotheses:
+	\begin{gather}
+		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6} \\
+		V_{13} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{7}
+	\end{gather}
+	We use \hyp{6} with valuation \(\sigma\) projected on the variables from generating transitions in \(A_2\) to get \nmm{\nu: \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
+	The left side of the implication is proved using \hyp{5a} and \hyp{5c} because the guards from transitions of \(A_2\) are still in transitions of \(A_{23}\), the right side gives:
+	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6'} \]
+	We then use \hyp{7} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}}}.
+	The left side of the implication is proved using \hyp{5b} and \hyp{6'}, the right side gives:
+	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{7'} \]
+	\goal{1} is proved for valuation \(\nu'\) by admitting the left side and using \hyp{7'}.
+\end{proof}
+
+\subsection{Congruence for composition}\label{apx:cong}
+
+\subsection{compatibility with FH-bisimulation}\label{apx:FHbcomp}
+
 \end{document}

### 2021-06-12 2021-Refinement/report.tex
All todos for finishing the report

@@
 
-% Related work: thesis
+% TODO: Related work: thesis
 
@@
 Section \ref{sec:refinement} introduces and analyses the refinement relation on open automata.
-% future work
-% conclusion
+Finally Section \ref{sec:ccl} recapitulates the contribution and present the work left.
 
@@
 \defitem Inital state is reachable: \(\sigma_0 \vdash \reach{A}\mpar{s_0}\)
-\defitem Reachability is preserved across transitions: \nmm{\bigsymb{\forall} t \defobject \OTg \in T, \fvars{t} \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}}
+\defitem Reachability is preserved across transitions: \nmm{\forall t \defobject \OTg \in T, \fvars{t} \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}}
 \end{defi}
@@
 Only one of the hole-\(\triangle\) simulations cannot tell that a non-locking composition with any automaton is a refinement because we need at the same time to add and remove holes, hence the need of the special composition correctness for hole-superset.
-ALso an issue arises when trying to tell that a composition is a refinement of the base automaton: the refinement relation cannot compare the holes sets.
+Also an issue arises when trying to tell that a composition is a refinement of the base automaton: the refinement relation cannot compare the holes sets.
 This conflicts with the transitivity propriety when a hole present in both extrema of the chain is absent in an intermediate automaton.
@@
 
-The transitivity property becomes \(\wrel{X}{A}{B} \wedge \wrel{Y}{B}{C} \implies \wrel{X \cap Y}{A}{C}\).
+The transitivity property becomes \(\wrel{A}{B}{X} \wedge \wrel{B}{C}{X} \implies \wrel{A}{C}{X \cap Y}\).
 It behaves the same as if the holes outside the intersection were renamed to avoid conflicts in the first place.
@@
 Proving them for the open automata refinement will also prove them for each hole-\(\triangle\) simulation as they are just restricted cases.
-% TODO: Explain two refinement steps comositions so that Correctness wrt composition is trivial
+
+\begin{thm} Open automata refinement is correct w.r.t.\@ composition \end{thm}
+We will decompose composition into two refinement steps, transitivity will complete the proof.
+Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OA[2]\) and \(k \in J_1\) such that \(A_1\subst{A_2}{k}\) is non-locking.
+We pose
+\begin{gather*}
+	A'_2 \defobject \OA{S_2}{s_{02}}{V_2}{\sigma_{02}}{\emptyset}{T'_2} \\
+	T'_2 \defobject \mset{\OT{s}{s'}{\alpha}{\mbrc{}}{g}{\psi}}{\OTg \in T_2}
+\end{gather*}
+By limited composition correctness we have \(\wrel{J_1 \setminus \mbrc{k}}{A_1\subst{A'_2}{k}}{A_1}\).
+Adding holes and binding actions to the new holes is a refinement for hole-superset simulation so we have \(\wrel{A_1\subst{A_2}{k}}{A_1\subst{A'_2}{k}}{J_1 \setminus \mbrc{k}}\).
+By transitivity we have composition correctness.
 \begin{thm}[Context refinement] Open automata refinement is context refining. \end{thm}
 Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\).
-Let \(k \in J_1 \cap J_2\), \(\mpar{R_{12}, H_{12}}\) be a hole-tracking simulation of \(A_1\) by \(A_2\) and \(\reach{A\subst{A_3}{k}}\) be a witness that \(A\subst{A_3}{k}\) is non-locking.
+Let \(k \in J_1 \cap J_2\), \(\mpar{R_{12}, H_{12}}\) be a hole-tracking simulation of \(A_1\) by \(A_2\) and \(\reach{A_1\subst{A_3}{k}}\) be a witness that \(A_1\subst{A_3}{k}\) is non-locking.
 The idea for the relation on configurations is that \(A_2\) simulates \(A_1\) while \(A_3\) does the same things in both compositions in the hole \(k\).
 \begin{gather*}
-	R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \\
+	R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_1\subst{A_3}{k}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \\
 	H \defobject J_3 \uplus H_{12} \setminus \mbrc{k}
@@
 Where \(y_{3x}\) is the renaming of \(y_3\) from \(A_3\) in \(A_x\subst{A_3}{k}\).
-\(\mpar{R, H}\) is a witness of \(\wrel{H}{A_{13}}{A_{23}}\), proof is given in Appendix \ref{apx:cr}.
-% TODO: Proof for Congruence \ref{apx:cong}
-% TODO: Proof for FH-bisimulation compatibility \ref{apx:FHbcomp}
+\(\mpar{R, H}\) is a witness of \(\wrel{H}{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}\), proof is given in Appendix \ref{apx:cr}.
+\begin{thm}[Composition congruence] Open automata refinement is congruent for composition \end{thm}
+Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\).
+Let \(k \in J_1\), \(\mpar{R_{23}, H_{23}}\) be a hole-tracking simulation of \(A_2\) by \(A_3\) and \(\reach{A_1\subst{A_2}{k}}\) be a witness that \(A_1\subst{A_2}{k}\) is non-locking.
+The idea for the relation on configurations is that \(A_3\) simulates \(A_2\) while \(A_1\) does the same things in both compositions.
+\begin{gather*}
+	R \defobject \mpar{\mpar{s_{12}, s_2}, \mpar{s_{13}, s_3}} \mapsto \choice{R_{23}\mpar{s_2, s_3} \wedge \reach{A_1\subst{A_2}{k}}\mpar{s_{12}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{13} = v_{23} & \text{if } s_{12} = s_{13} \\ \bot & \text{otherwise}} \\
+	H \defobject H_{23} \uplus J_1 \setminus \mbrc{k}
+\end{gather*}
+Where \(y_{1x}\) is the renaming of \(y_1\) from \(A_1\) in \(A_1\subst{A_x}{k}\).
+\(\mpar{R, H}\) is a witness of \(\wrel{H}{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}\), proof is given in Appendix \ref{apx:cong}.
+\begin{thm}[FH-bisimulation compatibility] Open automata refinement is compatible with FH-bisimulation \end{thm}
+The requirements of FH-bisimulation are strictly stronger than the open automata refinement so the transitivity proof is sufficient.
 
@@
 
-\section{Conclusion}
+\section{Conclusion}\label{sec:ccl}
 % TODO: recap contribs?
@@
 
-\subsection{compatibility with FH-bisimulation}\label{apx:FHbcomp}
-
 \end{document}

### 2021-06-13 2021-Refinement/report.tex
All proofs done

@@
 
-Formally for \(A = \OAg\), it gives
+Formally for \(\OAg \defobject A\), it gives
 \begin{multline*}
@@
 The main goal of this section is to explain the different aspects of refinement in restricted cases so that they are not all introduced at once in the real refinement relation.
-In particular if we have a family of open automata \(A_i \defobject \OAg[i]\), \(0 \leq i \leq n\), let \(A \defobject \OAg\) be such that \(A = A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\).
-Recall that there is no relation between the holes of \(A\) and \(A_0\) because \(J = \mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}\) is neither subset nor superset of \(J_0\).
+In particular if we have a family of open automata \(A_i \defobject \OAg[i]\), \(0 \leq i \leq n\), let \(A \defobject A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\).
+Recall that there is no relation between the holes of \(A\) and \(A_0\) because \(\mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}\) is neither subset nor superset of \(J_0\).
 So looking at restricted cases where holes are related in a specific manner can help understanding the general case.
@@
 
-Examples of application of the different refinement relations are given in Appendix \ref{apx:refrel}.
+Examples of application of the different refinement relations are given in Appendix \ref{apx:refrel}.% TODO: Maybe put them here, not in appendix
 \begin{thm} A hole-\(\triangle\) simulation is a pre-simulation. \end{thm}
@@
 		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\[12pt]
-		\quad \mpar{\forall x \in X, J'_{2x} \cap J_1 \cap H = J'_1 \cap J_2 \cap H} \\[-10pt]
+		\quad \mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H} \\[-10pt]
 		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2 \cap H} \beta_{1j} = \beta_{2xj} \\
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \\
 			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
@@
 Not renaming conflicting holes still have an interest.
-If we are trying to build an automaton \(A\) with several constraints \(A \leq B_i, i \in I\) -method B like- and each \(B_i\) is a refinement of some automaton \(C\) then we can have each \(B_i\) constrain a different subset of \(A\)'s holes.
-On each individual path \(A \leq B_i \leq C\), some holes of \(A\) are unconstrained but when considering all path they are all constrained.
+If we are trying to build an automaton \(A\) with several constraints \(\wrel{A}{B_i}{J_{Bi}}, i \in I\) -method B like- and each \(B_i\) is a refinement of some automaton \(C\) then we can have each \(B_i\) constrain a different subset of \(A\)'s holes.
+On each individual path \(A \leq_{J_{Bi}} B_i \leq_{J_{Bi}} C\), some holes of \(A\) are unconstrained but when considering all path they are all constrained.
+However this doesn't implies \(A \leq_{\bigcup_{i \in I} J_{Bi}} C\), it has to be checked separately.
+% TODO: maybe add an example here
 
@@
 Proving them for the open automata refinement will also prove them for each hole-\(\triangle\) simulation as they are just restricted cases.
-
 \begin{thm} Open automata refinement is correct w.r.t.\@ composition \end{thm}
 We will decompose composition into two refinement steps, transitivity will complete the proof.
-Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OA[2]\) and \(k \in J_1\) such that \(A_1\subst{A_2}{k}\) is non-locking.
+Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(k \in J_1\) such that \(A_1\subst{A_2}{k}\) is non-locking.
 We pose
@@
 \end{gather*}
-By limited composition correctness we have \(\wrel{J_1 \setminus \mbrc{k}}{A_1\subst{A'_2}{k}}{A_1}\).
+By limited composition correctness we have \(\wrel{A_1\subst{A'_2}{k}}{A_1}{J_1 \setminus \mbrc{k}}\).
 Adding holes and binding actions to the new holes is a refinement for hole-superset simulation so we have \(\wrel{A_1\subst{A_2}{k}}{A_1\subst{A'_2}{k}}{J_1 \setminus \mbrc{k}}\).
@@
 Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\).
-Let \(k \in J_1 \cap J_2\), \(\mpar{R_{12}, H_{12}}\) be a hole-tracking simulation of \(A_1\) by \(A_2\) and \(\reach{A_1\subst{A_3}{k}}\) be a witness that \(A_1\subst{A_3}{k}\) is non-locking.
+Let \(\mpar{R_{12}, H_{12}}\) be a hole-tracking simulation of \(A_1\) by \(A_2\), \(k \in H_{12}\) and \(\reach{A_1\subst{A_3}{k}}\) be a witness that \(A_1\subst{A_3}{k}\) is non-locking.
 The idea for the relation on configurations is that \(A_2\) simulates \(A_1\) while \(A_3\) does the same things in both compositions in the hole \(k\).
@@
 Where \(y_{3x}\) is the renaming of \(y_3\) from \(A_3\) in \(A_x\subst{A_3}{k}\).
-\(\mpar{R, H}\) is a witness of \(\wrel{H}{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}\), proof is given in Appendix \ref{apx:cr}.
+\(\mpar{R, H}\) is a witness of \(\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{H}\), proof is given in Appendix \ref{apx:cr}.
 \begin{thm}[Composition congruence] Open automata refinement is congruent for composition \end{thm}
@@
 \begin{gather*}
-	R \defobject \mpar{\mpar{s_{12}, s_2}, \mpar{s_{13}, s_3}} \mapsto \choice{R_{23}\mpar{s_2, s_3} \wedge \reach{A_1\subst{A_2}{k}}\mpar{s_{12}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{13} = v_{23} & \text{if } s_{12} = s_{13} \\ \bot & \text{otherwise}} \\
+	R \defobject \mpar{\mpar{s_{12}, s_2}, \mpar{s_{13}, s_3}} \mapsto \choice{R_{23}\mpar{s_2, s_3} \wedge \reach{A_1\subst{A_2}{k}}\mpar{s_{12}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{12} = v_{13} & \text{if } s_{12} = s_{13} \\ \bot & \text{otherwise}} \\
 	H \defobject H_{23} \uplus J_1 \setminus \mbrc{k}
@@
 Where \(y_{1x}\) is the renaming of \(y_1\) from \(A_1\) in \(A_1\subst{A_x}{k}\).
-\(\mpar{R, H}\) is a witness of \(\wrel{H}{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}\), proof is given in Appendix \ref{apx:cong}.
+\(\mpar{R, H}\) is a witness of \(\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{H}\), proof is given in Appendix \ref{apx:cong}.
 \begin{thm}[FH-bisimulation compatibility] Open automata refinement is compatible with FH-bisimulation \end{thm}
-The requirements of FH-bisimulation are strictly stronger than the open automata refinement so the transitivity proof is sufficient.
-
-% TODO: What happens on untracked holes (untracked holes equivalent behaviour => free variables; some sort of daisy equivalence)
+The requirements of FH-bisimulation are strictly stronger than the open automata refinement so using transitivity is sufficient.
+
+% TODO HERE: What happens on untracked holes (untracked holes equivalent behaviour => free variables; some sort of daisy equivalence)
 
@@
 It is a simplified version of the motivation for making a refinement relation, which is the traffic light system in an article about weak-bisimulation \cite{wang:03126313}.
-It had to be modified because here the simulation is a strong-simulation.
+It had to be modified because here the simulation is a strong-simulation (no silent actions).
 
@@
 Let \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\) be open automata, where \(J_2 = \emptyset\).
-Let \(k \in J_1\) and \(A \defobject A_1\subst{A_2}{k}\), with \(A = \OAg\).
+Let \(k \in J_1\) and \(A \defobject A_1\subst{A_2}{k}\), with \(\OAg \defobject A\).
 Let \(\reach{A}\) be a witness that \(A\) is non-locking.
@@
 	\goal{2c} is proved using \hyp{1c} (\(g \equiv g_1\) or \(g \equiv g_1 \wedge \dots\)).
-	For \goal{2d} we use \hyp{1a} with the preservation of reachability across transitions (+ \hyp{1b}), \hyp{1b} and the fact that the valuations coincide on the renamed values:
+	For \goal{2d} we use \hyp{1a} with the preservation of reachability across transitions, \hyp{1b} and the fact that the valuations coincide on the renamed values:
 	\begin{align*}
@@
 		\iff & \sigma \uplus \nu \vdash \reach{A}\mpar{s}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1} \psi_{1'}\mpar{v_{1'}} = \psi_1\mpar{v_1} \\
-		\iff & \sigma \uplus \nu \vdash \reach{A}\mpar{s}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1 \uplus \fvars{t_1}} v_{1'} = v_1 \\
+		\impliedby & \sigma \uplus \nu \vdash \reach{A}\mpar{s}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1 \uplus \fvars{t_1}} v_{1'} = v_1 \\
 		\iff & \mpar{\sigma \vdash \reach{A}\mpar{s}\psubst{\psi}} \wedge \mpar{\sigma \uplus \nu \vdash \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1}
@@
 Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) be open automata.
-Let \(k \in J_1 \setminus J_2\) and \(A \defobject A_1\subst{A_3}{k}\), with \(A = \OAg\).
+Let \(k \in J_1 \setminus J_2\) and \(A \defobject A_1\subst{A_3}{k}\), with \(\OAg \defobject A\).
 Let \(R_{12}\) be a hole-superset simulation of \(A_1\) by \(A_2\) and \(\reach{A}\) be a witness that \(A\) is non-locking.
@@
 		\forall z \in Z_{s2x}, J'_{3z} \cap J_2 = J'_{s2x} \cap J_3 \hyp{1x} \\
-		V_2 \uplus V_3 \uplus \fvars{t_{s2x}} \vdash R_{23}\mpar{s_2, s_3} \wedge g_{s2x} \Rightarrow \operatorname*{\bigsymb{\bigvee}}_\subbox{z \in Z_{s2x}} \mpar{\!\everymath{\displaystyle}\begin{array}{l}
+		V_2 \uplus V_3 \uplus \fvars{t_{s2x}} \vdash R_{23}\mpar{s_2, s_3} \wedge g_{s2x} \implies \operatorname*{\bigsymb{\bigvee}}_\subbox{z \in Z_{s2x}} \mpar{\everymath{\displaystyle}\begin{array}{l}
 			\alpha_{s2x} = \alpha_{3z} \wedge \bigwedge_\subbox{j \in J'_{3z} \cap J_2} \beta_{s2xj} = \beta_{3zj} \\[12pt]
 			\nwedge g_{3z} \wedge R_{23}\mpar{s'_{s2x}, s'_{3z}}\psubst{\psi_{s2x} \uplus \psi_{3z}}
-		\end{array}\!} \hyp{1x'}
+		\end{array}} \hyp{1x'}
 	\end{gather*}
@@
 
-\subsection{Context refinement}\label{apx:cr} % TODO HERE: adapt
-Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) be three open automata.
-Let \(k \in J_1\), \(A_{13} \defobject A_1\subst{A_3}{k}\) and \(A_{23} \defobject A_2\subst{A_3}{k}\).
-Let \(R_{12}\) be a hole-equal simulation of \(A_1\) by \(A_2\) and \(\reach{A_{13}}\) be a witness that \(A_{13}\) is non-locking.
-We pose \(A_{13} = \OAg[13]\) and \(A_{23} = \OAg[23]\).
-\[ R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \]
+\subsection{Context refinement}\label{apx:cr}
+Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) and \(\mpar{R_{12}, H_{12}}\) be a hole-tracking simulation of \(A_1\) by \(A_2\).
+Let \(k \in H_{12}\), \(A_{13} \defobject A_1\subst{A_3}{k}\), \(A_{23} \defobject A_2\subst{A_3}{k}\) and \(\reach{A_{13}}\) be a witness that \(A_{13}\) is non-locking.
+We pose \(\OAg[13] \defobject A_{13}\) and \(\OAg[23] \defobject A_{23}\).
+\begin{gather*}
+	R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \\
+	H \defobject J_3 \uplus H_{12} \setminus \mbrc{k}
+\end{gather*}
 Where \(y_{3x}\) is the renaming of \(y_3\) from \(A_3\) in \(A_{x3}\).
-We want to prove that \(R\) is a hole-equal simulation of \(A_{12}\) by \(A_{23}\).
+We want to prove that \(\mpar{R, H}\) is a witness of \(\wrel{A_{13}}{A_{23}}{H}\).
 \begin{proof}
-\item[1)] \(J_{13} = J_3 \uplus J_1 \setminus \mbrc{k} = J_3 \uplus J_2 \setminus \mbrc{k} = J_{23}\) by \(J_1 = J_2\).
-\item[2)] For \(\sigma_{013} \uplus \sigma_{023} \vdash R\mpar{s_{013}, s_{023}}\) we use the fact that \(R_{12}\) relates inital configurations and initial configuration is reachable:
+\item[1)] \(H = J_3 \uplus H_{12} \setminus \mbrc{k} \subseteq J_3 \uplus \mpar{J_1 \cap J_2} \setminus \mbrc{k} = \mpar{J_3 \uplus J_1 \setminus \mbrc{k}} \cap \mpar{J_3 \uplus J_2 \setminus \mbrc{k}} = J_{13} \cap J_{23}\)
+\item[2)] We use the fact that \(R_{12}\) relates inital configurations, initial configuration is reachable, and \(\sigma_{031}\) and \(\sigma_{032}\) are renaming of \(\sigma_{03}\):
 	\begin{align*}
@@
 		& \bigsymb{\forall} t_{13} \defobject \OTx{13}{}{13}{13} \in \fOT{s_{13}}, \bigsymb{\exists} \mpar{t_{23x} \defobject \OTx{23}{x}{23x}{23x} \in \fOT{s_{23}}}^{x \in X}, \\
-		& \quad \mpar{\forall x \in X, J'_{23x} \cap J_{13} = J'_{13} \cap J_{23}} \\[-10pt]
-		& \nwedge V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \Rightarrow \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\!\!\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \\[12pt]
+		& \quad \mpar{\forall x \in X, J'_{23x} \cap H = J'_{13} \cap H} \\[-10pt]
+		& \nwedge V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H} \beta_{13j} = \beta_{23xj} \\[12pt]
 			\nwedge g_{23x} \wedge R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
-		\end{array}\!\!} \goal{0}
+		\end{array}} \goal{0}
 	\end{align*}
@@
 		& \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
-		& \quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
-		& \nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		& \quad \mpar{\forall x \in X, J'_{2x} \cap H_{12} = J'_1 \cap H_{12}} \\[-10pt]
+		& \nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R_{12}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H_{12}} \beta_{1j} = \beta_{2xj} \\[12pt]
+			\nwedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
 		\end{array}} \hyp{1}
@@
 		\mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X} \\
-		\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2 \hyp{1'} \\
-		V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\forall x \in X, J'_{2x} \cap H_{12} = J'_1 \cap H_{12} \hyp{1'} \\
+		V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R_{12}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H_{12}} \beta_{1j} = \beta_{2xj} \\[12pt]
+			\nwedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
 		\end{array}} \hyp{1"}
 	\end{gather*}
-	To build the family of transitions we need to know if \(k \in J'_{2x}\) for a every \(x \in X\):
-	\begin{align*}
-		J'_1 & = J'_1 \cap J_1 \\
-		& = J'_1 \cap J_2 & \text{by } J_1 = J_2 \\
-		& = J'_{2x} \cap J_1 & \text{by \hyp{1'}} \\
-		& = J'_{2x} \cap J_2 & \text{by } J_1 = J_2 \\
-		& = J'_{2x} \hyp{2}
-	\end{align*}
-	In the case \(s_{31} \neq s_{32}\) we can give the empty family, it won't cause any issue.
-	Otherwise \(s_{31} = s_{32}\) so we can copy \(t_{31}\) into \nmm{t_{32} = \OTx{32}{}{32}{32}} to avoid conflicts.
+	To build the family of transitions we need to know if \(k \in J'_{2x}\) for a every \(x \in X\).
+	We have \(k \in H_{12}\) so by \hyp{1'} \(k \in J'_{2x} \iff k \in J'_1\).
+	If \(s_{31} = s_{32}\) we can copy \(t_{31}\) into \nmm{t_{32} = \OTx{32}{}{32}{32}} to avoid conflicts.
 	We also name \(t_3\) the original transition from \(T_3\).
-	Using \hyp{2} we can build the familly of transition generated by the family \(t_{2x}^{x \in X}\):
+	We build the familly of transition generated by the family \(t_{2x}^{x \in X}\):
 	\[ t_{23x}^{x \in X} \defobject x \mapsto \choice{
@@
 	} \]
+	Otherwise \(s_{31} \neq s_{32}\) and we can give the empty family, it won't cause any issue.
 	We will prove \goal{0} for the family \(t_{23x}^{x \in X}\), the new goals are
 	\begin{gather}
-		\forall x \in X, J'_{23x} \cap J_{13} = J'_{13} \cap J_{23} \goal{0'} \\
+		\forall x \in X, J'_{23x} \cap H = J'_{13} \cap H \goal{0'} \\
 		V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \\[12pt]
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{13} \cap H} \beta_{13j} = \beta_{23xj} \\[12pt]
 			\nwedge g_{23x} \wedge R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
@@
 	\end{gather}
-\item[\goal{0'}:] Let \(x \in X\), by case on \(k \in J'_1\):
-	\begin{align*}
-		\text{If } k \in J'_1: && J'_{23x} \cap J_{13} & = \mpar{J'_{31} \uplus J'_{2x} \setminus \mbrc{k}} \cap \mpar{J_3 \uplus J_1 \setminus \mbrc{k}} \\
-		&&& = \mpar{J'_{31} \cap J_3} \uplus \mpar{J'_{2x} \cap J_1} \setminus \mbrc{k} \\
-		&&& = \mpar{J'_{31} \cap J_3} \uplus \mpar{J'_1 \cap J_2} \setminus \mbrc{k} & \text{by \hyp{1'}} \\
-		&&& = \mpar{J'_{31} \uplus J'_1 \setminus \mbrc{k}} \cap \mpar{J_3 \uplus J_2 \setminus \mbrc{k}} \\
-		&&& = J'_{13} \cap J_{23} \\
-		\text{If } k \notin J'_1: && J'_{23x} \cap J_{13} & = \mpar{J'_{2x} \setminus \mbrc{k}} \cap \mpar{J_1 \setminus \mbrc{k}} \\
-		&&& = J'_{2x} \cap J_1 & \text{by } k \notin J'_1 = J'_{2x} \text{ \hyp{2}} \\
-		&&& = J'_1 \cap J_2 & \text{by \hyp{1'}} \\
-		&&& = \mpar{J'_1 \setminus \mbrc{k}} \cap \mpar{J_2 \setminus \mbrc{k}} & \text{by } k \notin J'_1 \\
-		&&& = J'_{13} \cap J_{23}
+\item[\goal{0'}:] Let \(x \in X\), by case on \(k \in J'_1\).
+	\begin{align*}
+		\text{If } k \in J'_1: && J'_{23x} \cap H & = \mpar{J'_{32} \uplus J'_{2x} \setminus \mbrc{k}} \cap \mpar{J_3 \uplus H_{12} \setminus \mbrc{k}} \\
+		&&& = \mpar{J'_{31} \cap J_3} \uplus \mpar{J'_{2x} \cap H_{12}} \setminus \mbrc{k} & \text{by } J'_{32} = J'_{31} \\
+		&&& = \mpar{J'_{31} \cap J_3} \uplus \mpar{J'_1 \cap H_{12}} \setminus \mbrc{k} & \text{by \hyp{1'}} \\
+		&&& = \mpar{J'_{31} \uplus J'_1 \setminus \mbrc{k}} \cap \mpar{J_3 \uplus H_{12} \setminus \mbrc{k}} \\
+		&&& = J'_{13} \cap H \\
+		\text{If } k \notin J'_1: && J'_{23x} \cap H & = \mpar{J'_{2x} \setminus \mbrc{k}} \cap \mpar{J_3 \uplus H_{12} \setminus \mbrc{k}} \\
+		&&& = \mpar{J'_{2x} \cap H_{12}} \setminus \mbrc{k} \\
+		&&& = \mpar{J'_1 \cap H_{12}} \setminus \mbrc{k} & \text{by \hyp{1'}} \\
+		&&& = \mpar{J'_1 \setminus \mbrc{k}} \cap \mpar{J_3 \uplus H_{12} \setminus \mbrc{k}} \\
+		&&& = J'_{13} \cap H
 	\end{align*}
@@
 	We use dummy values for the variables in \nmm{\biguplus_{x \in X} \fvars{t_{23x}}} to get the left side of the implication as an hypothesis (independant from these values):
-	\[ \sigma \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \hyp{3} \]
+	\[ \sigma \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \hyp{2} \]
 	If \(s_{31} \neq s_{32}\) then this hypothesis is \(\sigma \vdash \bot\), the empty family works and the proof is finished.
-	We can assume \(s_{31} = s_{32}\) and break \hyp{3} into
-	\begin{gather}
-		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{3a} \\
-		\sigma \vdash \reach{A_{13}}\mpar{s_{13}} \hyp{3b} \\
-		\sigma \vdash \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} \hyp{3c} \\
-		\sigma \vdash g_{13} \hyp{3d}
+	We can assume \(s_{31} = s_{32}\) and break \hyp{2} into
+	\begin{gather}
+		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{2a} \\
+		\sigma \vdash \reach{A_{13}}\mpar{s_{13}} \hyp{2b} \\
+		\sigma \vdash \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} \hyp{2c} \\
+		\sigma \vdash g_{13} \hyp{2d}
 	\end{gather}
@@
 	Then we get the values of the implicit \(\exists\) in \nmm{\nu: \biguplus_{x \in X} \fvars{t_{2x}}}.
-	The left side of the implication is proved with \hyp{3a} and \hyp{3d}.
+	The left side of the implication is proved with \hyp{2a} and \hyp{2d}.
 	So we get a \(x \in X\) such that
 	\begin{gather}
-		\sigma \uplus \nu \vdash \alpha_1 = \alpha_{2x} \hyp{4a} \\
-		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \hyp{4b} \\
-		\sigma \uplus \nu \vdash g_{2x} \hyp{4c} \\
-		\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \hyp{4d}
-	\end{gather}
-	If \(k \in J'_1\), we extend the valuation \(\nu\) to cover the variables of \(t_3\) in \(t_{23x}\) using their value in \(t_{13}\), \(\nu' \defobject \nu \uplus \mset{v_{32} \mapsto \sigma\mpar{v_{31}}}{v_3 \in \fvars{t_3}}\)
+		\sigma \uplus \nu \vdash \alpha_1 = \alpha_{2x} \hyp{3a} \\
+		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \hyp{3b} \\
+		\sigma \uplus \nu \vdash g_{2x} \hyp{3c} \\
+		\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \hyp{3d}
+	\end{gather}
+	If \(k \in J'_1\), we extend the valuation \(\nu\) to cover the variables of \(t_3\) in \(t_{23x}\) using their value in \(t_{13}\), \(\nu' \defobject \nu \uplus \mset{v_{32} \mapsto \sigma\mpar{v_{31}}}{v_3 \in \fvars{t_3}}\).
 	Otherwise \(\nu' \defobject \nu\).
@@
 		\sigma \uplus \nu' \vdash \alpha_{13} = \alpha_{23x} \goal{3a} \\
-		\sigma \uplus \nu' \vdash \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \goal{3b} \\
+		\sigma \uplus \nu' \vdash \bigwedge_\subbox{j \in J'_{23x} \cap H} \beta_{13j} = \beta_{23xj} \goal{3b} \\
 		\sigma \uplus \nu' \vdash g_{23x} \goal{3c} \\
@@
 	\end{gather}
-	Because composition doesn't change the produced actions nor its variables, \goal{3a} is proved by \hyp{4a}.
-	\goal{3b} holds because the valuations for the actions of the holes in \(J_3\) coincide by definition of \(\nu'\) and by \hyp{4b} for the others.
-	For \goal{3c} we have two cases, if \(k \notin J'_1\) then \(g_{23x} \equiv g_{2x}\) and \hyp{4c} is sufficient, if \(k \in J'_1\) then \(g_{23x} \equiv g_{2x} \wedge g_3 \wedge \alpha_3 = \beta_{2xk}\) so we also need \hyp{3d} (\(g_{13} \equiv g_1 \wedge g_3 \wedge \alpha_3 = \beta_{1k}\)) and \hyp{4b} for the value \(k\) (\(\beta_{1k} = \beta_{2xk}\)).
-	\goal{3d} is proved using \hyp{4d}, \hyp{3b} with the preservation of reachability across transitions (+ \hyp{3d}), \hyp{3c} and the fact that \(A_3\) performs the same transition with same values in both composed automata:
+	Because composition doesn't change the produced actions nor its variables, \goal{3a} is proved by \hyp{3a}.
+	\goal{3b} holds because the valuations for the actions of the holes in \(J_3\) coincide by definition of \(\nu'\) and by \hyp{3b} for the others.
+	For \goal{3c} we have two cases, if \(k \notin J'_1\) then \(g_{23x} \equiv g_{2x}\) and \hyp{3c} is sufficient, if \(k \in J'_1\) then \(g_{23x} \equiv g_{2x} \wedge g_3 \wedge \alpha_3 = \beta_{2xk}\) so we also need \hyp{2d} (\(g_{13} \equiv g_1 \wedge g_3 \wedge \alpha_3 = \beta_{1k}\)) and \hyp{3b} for the value \(k\) (\(\beta_{1k} = \beta_{2xk}\)).
+	\goal{3d} is proved using \hyp{3d}, \hyp{2b} with the preservation of reachability across transitions (+ \hyp{2d}), \hyp{2c} and the fact that \(A_3\) performs the same transition with same values in both composed automata:
 	\begin{align*}
@@
 		\iff & \sigma \uplus \nu' \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}} \wedge \bigwedge_\subbox{v_3 \in V_3} \psi_{31}\mpar{v_{31}} = \psi_{32}\mpar{v_{32}} \\
-		\iff & \sigma \uplus \nu' \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}} \wedge \bigwedge_\subbox{v_3 \in V_3 \uplus \fvars{t_3}} v_{31} = v_{32} \\
+		\impliedby & \sigma \uplus \nu' \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}} \wedge \bigwedge_\subbox{v_3 \in V_3 \uplus \fvars{t_3}} v_{31} = v_{32} \\
 		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}}} \wedge \mpar{\sigma \vdash \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32}}
@@
 	\begin{gather}
-		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{5a} \\
-		\sigma \vdash \reach{A_{13}}\mpar{s_{13}} \hyp{5b} \\
-		\sigma \vdash \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \hyp{5c}
+		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{4a} \\
+		\sigma \vdash \reach{A_{13}}\mpar{s_{13}} \hyp{4b} \\
+		\sigma \vdash \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \hyp{4c}
 	\end{gather}
@@
 	\begin{gather}
-		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6} \\
-		V_{13} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{7}
-	\end{gather}
-	We use \hyp{6} with valuation \(\sigma\) projected on the variables from generating transitions in \(A_2\) to get \nmm{\nu: \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
-	The left side of the implication is proved using \hyp{5a} and \hyp{5c} because the guards from transitions of \(A_2\) are still in transitions of \(A_{23}\), the right side gives:
-	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6'} \]
-	We then use \hyp{7} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}}}.
-	The left side of the implication is proved using \hyp{5b} and \hyp{6'}, the right side gives:
-	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{7'} \]
-	\goal{1} is proved for valuation \(\nu'\) by admitting the left side and using \hyp{7'}.
+		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{5} \\
+		V_{13} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{6}
+	\end{gather}
+	We use \hyp{5} with valuation \(\sigma\) projected on the variables from generating transitions in \(A_2\) to get \nmm{\nu: \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
+	The left side of the implication is proved using \hyp{4a} and \hyp{4c} because the guards from transitions of \(A_2\) are still in transitions of \(A_{23}\), the right side gives:
+	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{5'} \]
+	We then use \hyp{6} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}}}.
+	The left side of the implication is proved using \hyp{4b} and \hyp{5'}, the right side gives:
+	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{6'} \]
+	\goal{1} is proved for valuation \(\nu'\) by admitting the left side and using \hyp{6'}.
 \end{proof}
@@
 \subsection{Congruence for composition}\label{apx:cong}
+Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) be three open automata.
+Let \(k \in J_1\), \(\mpar{R_{23}, H_{23}}\) be a hole-tracking simulation of \(A_2\) by \(A_3\) and \(\reach{A_1\subst{A_2}{k}}\) be a witness that \(A_1\subst{A_2}{k}\) is non-locking.
+We pose \(\OAg[21] \defobject A_{21}\) and \(\OAg[31] \defobject A_{31}\).
+\begin{gather*}
+	R \defobject \mpar{\mpar{s_{12}, s_2}, \mpar{s_{13}, s_3}} \mapsto \choice{R_{23}\mpar{s_2, s_3} \wedge \reach{A_{21}}\mpar{s_{12}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{12} = v_{13} & \text{if } s_{12} = s_{13} \\ \bot & \text{otherwise}} \\
+	H \defobject H_{23} \uplus J_1 \setminus \mbrc{k}
+\end{gather*}
+Where \(y_{1x}\) is the renaming of \(y_1\) from \(A_1\) in \(A_{x1}\).
+We want to prove that \(\mpar{R, H}\) is a witness of \(\wrel{A_{21}}{A_{31}}{H}\).
+\begin{proof}
+\item[1)] \(H = H_{23} \uplus J_1 \setminus \mbrc{k} \subseteq \mpar{J_2 \cap J_3} \uplus J_1 \setminus \mbrc{k} = \mpar{J_2 \uplus J_1 \setminus \mbrc{k}} \cap \mpar{J_3 \uplus J_1 \setminus \mbrc{k}} = J_{21} \cap J_{31}\)
+\item[2)] We use the fact that \(R_{23}\) relates inital configurations, initial configuration is reachable, and \(\sigma_{012}\) and \(\sigma_{013}\) are renaming of \(\sigma_{01}\):
+	\begin{align*}
+		& \sigma_{021} \uplus \sigma_{031} \vdash R\mpar{s_{021}, s_{031}} \\
+		\iff & R\mpar{\mpar{s_{012}, s_{02}}, \mpar{s_{013}, s_{03}}}\psubst{\sigma_{012} \uplus \sigma_{02} \uplus \sigma_{013} \uplus \sigma_{03}} \\
+		\iff & R_{23}\mpar{s_{02}, s_{03}}\psubst{\sigma_{02} \uplus \sigma_{03}} \wedge \reach{A_{21}}\mpar{s_{021}}\psubst{\sigma_{021}} \wedge \mpar{\bigwedge_{v_1 \in V_1} v_{12} = v_{13}}\psubst{\sigma_{012} \uplus \sigma_{013}} \\
+		\iff & \mpar{\sigma_{02} \uplus \sigma_{03} \vdash R_{23}\mpar{s_{02}, s_{03}}} \wedge \mpar{\sigma_{021} \vdash \reach{A_{21}}\mpar{s_{021}}} \wedge \bigwedge_\subbox{v_1 \in V_1} \sigma_{012}\mpar{v_{12}} = \sigma_{013}\mpar{v_{13}} \\
+		\iff & \mpar{\sigma_{02} \uplus \sigma_{03} \vdash R_{23}\mpar{s_{02}, s_{03}}} \wedge \mpar{\sigma_{021} \vdash \reach{A_{21}}\mpar{s_{021}}} \wedge \top
+	\end{align*}
+\item[3)] Let \(s_{21} \defobject \mpar{s_{12}, s_2} \in S_{21}\) and \(s_{31} \defobject \mpar{s_{13}, s_3} \in S_{31}\).
+	We want to prove both
+	\begin{align*}
+		& \bigsymb{\forall} t_{21} \defobject \OTx{21}{}{21}{21} \in \fOT{s_{21}}, \bigsymb{\exists} \mpar{t_{31x} \defobject \OTx{31}{x}{31x}{31x} \in \fOT{s_{31}}}^{x \in X}, \\
+		& \quad \mpar{\forall x \in X, J'_{31x} \cap H = J'_{21} \cap H} \\[-10pt]
+		& \nwedge V_{21} \uplus V_{31} \uplus \fvars{t_{21}} \vdash R\mpar{s_{21}, s_{31}} \wedge g_{21} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{21} = \alpha_{31x} \wedge \bigwedge_\subbox{j \in J'_{31x} \cap H} \beta_{21j} = \beta_{31xj} \\[12pt]
+			\nwedge g_{31x} \wedge R\mpar{s'_{21}, s'_{31x}}\psubst{\psi_{21} \uplus \psi_{31x}}
+		\end{array}} \goal{0}
+	\end{align*}
+	\[ V_{21} \uplus V_{31} \uplus \biguplus_\subbox{t_{31} \in \fOT{s_{31}}} \fvars{t_{31}} \vdash R\mpar{s_{21}, s_{31}} \wedge \bigvee_\subbox{t_{31} \in \fOT{s_{31}}} \fguard{t_{31}} \implies \bigvee_\subbox{t_{21} \in \fOT{s_{21}}} \fguard{t_{21}} \goal{1} \]
+	Let \nmm{t_{21} \defobject \OTx{21}{}{21}{21} \in \fOT{s_{21}}}, it is obtained by composition of \nmm{t_{12} \defobject \OTx{12}{}{12}{12} \in \fOT{s_{12}}} and \nmm{t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}} if \(k \in J'_{12}\) or by a the first transition and the state \(s_2\) if \(k \notin J'_{12}\).
+	If \(k \in J'_{12}\), we use the fact that \(R_{23}\) is a simulation from the states \(\mpar{s_2, s_3}\) to get the hypothesis:
+	\begin{align*}
+		& \bigsymb{\forall} t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \bigsymb{\exists} \mpar{t_{3x} \defobject \OTx{3}{x}{3x}{3x} \in \fOT{s_3}}^{x \in X}, \\
+		& \quad \mpar{\forall x \in X, J'_{3x} \cap H_{23} = J'_2 \cap H_{23}} \\[-10pt]
+		& \nwedge V_2 \uplus V_3 \uplus \fvars{t_2} \vdash R_{23}\mpar{s_2, s_3} \wedge g_2 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_2 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x} \cap H_{23}} \beta_{2j} = \beta_{3xj} \\[12pt]
+			\nwedge g_{3x} \wedge R_{23}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
+		\end{array}} \hyp{1}
+	\end{align*}
+	hypothesis that we use with the transition \(t_2\) to get
+	\begin{gather*}
+		\mpar{t_{3x} \defobject \OTx{3}{x}{3x}{3x} \in \fOT{s_3}}^{x \in X} \\
+		\forall x \in X, J'_{3x} \cap H_{23} = J'_2 \cap H_{23} \hyp{1'} \\
+		V_2 \uplus V_3 \uplus \fvars{t_2} \vdash R_{23}\mpar{s_2, s_3} \wedge g_2 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_2 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x} \cap H_{23}} \beta_{2j} = \beta_{3xj} \\[12pt]
+			\nwedge g_{3x} \wedge R_{23}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
+		\end{array}} \hyp{1"}
+	\end{gather*}
+	In the case \(s_{12} \neq s_{13}\) we can give the empty family, it won't cause any issue.
+	Otherwise \(s_{12} = s_{13}\) so we can copy \(t_{12}\) into \nmm{t_{13} = \OTx{13}{}{13}{13}} to avoid conflicts.
+	We also name \(t_1\) the original transition from \(T_1\).
+	We build the familly of transition generated by \(t_{13}\):
+	\[ t_{31x}^{x \in X} \defobject \choice{
+		x \mapsto \OT{\mpar{s_{13}, s_3}}{\mpar{s'_{13}, s'_{3x}}}{\alpha_{13}}{\beta_{13j}^{j \in J'_{13x} \setminus \mbrc{k}} \uplus \beta_{3xj}^{j \in J'_{3x}}}{g_{13} \wedge g_{3x} \wedge \alpha_{3x} = \beta_{13k}}{\psi_{13} \uplus \psi_{3x}} & \text{if } k \in J'_{13} \\
+		x \mapsto \OT{\mpar{s_{13}, s_3}}{\mpar{s'_{13}, s_3}}{\alpha_{13}}{\beta_{13j}^{j \in J'_{13}}}{g_{13}}{\psi_{13}} & \text{otherwise}
+	} \]
+	We will prove \goal{0} for the family \(t_{31x}^{x \in X}\), the new goals are
+	\begin{gather}
+		\forall x \in X, J'_{31x} \cap H = J'_{21} \cap H \goal{0'} \\
+		V_{21} \uplus V_{31} \uplus \fvars{t_{21}} \vdash R\mpar{s_{21}, s_{31}} \wedge g_{21} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{21} = \alpha_{31x} \wedge \bigwedge_\subbox{j \in J'_{31x} \cap H} \beta_{21j} = \beta_{31xj} \\[12pt]
+			\nwedge g_{31x} \wedge R\mpar{s'_{21}, s'_{31x}}\psubst{\psi_{21} \uplus \psi_{31x}}
+		\end{array}} \goal{2}
+	\end{gather}
+\item[\goal{0'}:] Let \(x \in X\), by case on \(k \in J'_{12}\).
+	\begin{align*}
+		\text{If } k \in J'_{12}: && J'_{31x} \cap H & = \mpar{J'_{3x} \uplus J'_{13} \setminus \mbrc{k}} \cap \mpar{H_{23} \uplus J_1 \setminus \mbrc{k}} \\
+		&&& = \mpar{J'_{3x} \cap H_{23}} \uplus \mpar{J'_{12} \cap J_1} \setminus \mbrc{k} & \text{by } J'_{13} = J'_{12} \\
+		&&& = \mpar{J'_2 \cap H_{23}} \uplus \mpar{J'_{12} \cap J_1} \setminus \mbrc{k} & \text{by \hyp{1'}} \\
+		&&& = \mpar{J'_2 \uplus J'_{12} \setminus \mbrc{k}} \cap \mpar{H_{23} \uplus J_1 \setminus \mbrc{k}} \\
+		&&& = J'_{32} \cap H \\
+		\text{If } k \notin J'_{12}: && J'_{31x} \cap H & = \mpar{J'_{13} \setminus \mbrc{k}} \cap \mpar{H_{23} \uplus J_1 \setminus \mbrc{k}} \\
+		&&& = \mpar{J'_{12} \setminus \mbrc{k}} \cap \mpar{H_{23} \uplus J_1 \setminus \mbrc{k}} \\
+		&&& = J'_{32} \cap H
+	\end{align*}
+\item[\goal{2}:] Let \(\sigma: V_{21} \uplus V_{31} \uplus \fvars{t_{21}} \to \values\).
+	We use dummy values for the variables in \nmm{\biguplus_{x \in X} \fvars{t_{31x}}} to get the left side of the implication as an hypothesis (independant from these values):
+	\[ \sigma \vdash R\mpar{s_{21}, s_{31}} \wedge g_{21} \hyp{2} \]
+	If \(s_{12} \neq s_{13}\) then this hypothesis is \(\sigma \vdash \bot\), the empty family works and the proof is finished.
+	We can assume \(s_{12} = s_{13}\) and break \hyp{2} into
+	\begin{gather}
+		\sigma \vdash R_{23}\mpar{s_2, s_3} \hyp{2a} \\
+		\sigma \vdash \reach{A_{21}}\mpar{s_{21}} \hyp{2b} \\
+		\sigma \vdash \bigwedge_\subbox{v_1 \in V_1} v_{12} = v_{13} \hyp{2c} \\
+		\sigma \vdash g_{21} \hyp{2d}
+	\end{gather}
+	If \(k \in J'_{12}\), we use \hyp{1"} with valuation \(\sigma\) on variables \(V_2 \uplus V_3 \uplus \fvars{t_2}\), then we get the values of the implicit \(\exists\) in \nmm{\nu: \biguplus_{x \in X} \fvars{t_{3x}}}.
+	The left side of the implication is proved with \hyp{2a} and \hyp{2d}.
+	So we get a \(x \in X\) such that
+	\begin{gather}
+		\sigma \uplus \nu \vdash \alpha_2 = \alpha_{3x} \hyp{3a} \\
+		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj} \hyp{3b} \\
+		\sigma \uplus \nu \vdash g_{3x} \hyp{3c} \\
+		\sigma \uplus \nu \vdash R_{23}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}} \hyp{3d}
+	\end{gather}
+	if \(k \notin J'_{12}\) we pose \(\nu \defobject \mbrc{}\) the empty valuation.
+	We extend the valuation \(\nu\) to cover the variables of \(t_{13}\) in \(t_{31x}\) using their value in \(t_{12}\), \(\nu' \defobject \nu \uplus \mset{v_{13} \mapsto \sigma\mpar{v_{12}}}{v_1 \in \fvars{t_1}}\)
+	We progress on \goal{2} by giving the valuation \(\sigma \uplus \nu'\) to the implicit \(\exists\), admitting the left side of the implication and choosing to prove the branch \(x\) of the disjunction:
+	\begin{gather}
+		\sigma \uplus \nu' \vdash \alpha_{21} = \alpha_{31x} \goal{3a} \\
+		\sigma \uplus \nu' \vdash \bigwedge_\subbox{j \in J'_{31x} \cap H} \beta_{21j} = \beta_{31xj} \goal{3b} \\
+		\sigma \uplus \nu' \vdash g_{31x} \goal{3c} \\
+		\sigma \uplus \nu' \vdash R\mpar{s'_{21}, s'_{31x}}\psubst{\psi_{21} \uplus \psi_{31x}} \goal{3d}
+	\end{gather}
+	Because composition doesn't change the produced actions nor its variables, \goal{3a} is proved by reflexivity.
+	\goal{3b} holds because the valuations for the actions of the holes in \(J_1\) coincide by definition of \(\nu'\) and by \hyp{3b} for the others (\(k \notin H\)).
+	For \goal{3c} we have two cases, if \(k \notin J'_{12}\) then \(g_{31x} \equiv g_{13}\) and \hyp{2d} is sufficient (\(g_{21} \equiv g_{13}\)), if \(k \in J'_{13}\) then \(g_{31x} \equiv g_{13} \wedge g_{3x} \wedge \alpha_{3x} = \beta_{13k}\) so we also need \hyp{3c} and \hyp{3a} in addition to \hyp{2d} (\(g_{21} \equiv g_{13} \wedge \alpha_2 = \beta_{12k}\)).
+	\goal{3d} is proved using \hyp{3d}, \hyp{2b} with the preservation of reachability across transitions (+ \hyp{2d}), \hyp{2c} and the fact that \(A_1\) performs the same transition with same values in both composed automata:
+	\begin{align*}
+		& \sigma \uplus \nu' \vdash R\mpar{s'_{21}, s'_{31x}}\psubst{\psi_{21} \uplus \psi_{31x}} \\
+		\iff & \sigma \uplus \nu' \vdash \mpar{R_{23}\mpar{s'_2, s'_{3x}} \wedge \reach{A_{21}}\mpar{s'_{21}} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{12} = v_{13}}\psubst{\psi_{12} \uplus \psi_2 \uplus \psi_{13} \uplus \psi_{3x}} \\
+		\iff & \sigma \uplus \nu' \vdash R_{23}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}} \wedge \reach{A_{21}}\mpar{s'_{21}}\psubst{\psi_{21}} \wedge \bigwedge_\subbox{v_1 \in V_1} \psi_{12}\mpar{v_{12}} = \psi_{13}\mpar{v_{13}} \\
+		\impliedby & \sigma \uplus \nu' \vdash R_{23}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}} \wedge \reach{A_{21}}\mpar{s'_{21}}\psubst{\psi_{21}} \wedge \bigwedge_\subbox{v_1 \in V_1 \uplus \fvars{t_1}} v_{12} = v_{13} \\
+		\iff & \mpar{\sigma \uplus \nu \vdash R_{23}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}} \wedge \mpar{\sigma \vdash \reach{A_{21}}\mpar{s'_{21}}\psubst{\psi_{21}}} \wedge \mpar{\sigma \vdash \bigwedge_\subbox{v_1 \in V_1} v_{12} = v_{13}}
+	\end{align*}
+\item[\goal{1}:] Let \nmm{\sigma: V_{21} \uplus V_{31} \uplus \biguplus_\subbox{t_{31} \in \fOT{s_{31}}} \fvars{t_{31}} \to \values}.
+	We use dummy values for the variables in \nmm{\biguplus_\subbox{t_{21} \in \fOT{s_{21}}} \fvars{t_{21}}} to get the left side of the implication (independant from these values), immediately broken into
+	\begin{gather}
+		\sigma \vdash R_{23}\mpar{s_2, s_3} \hyp{4a} \\
+		\sigma \vdash \reach{A_{21}}\mpar{s_{21}} \hyp{4b} \\
+		\sigma \vdash \bigvee_\subbox{t_{31} \in \fOT{s_{31}}} \fguard{t_{31}} \hyp{4c}
+	\end{gather}
+	\(R_{23}\) is a simulation and \(\reach{A_{21}}\) is a witness of the non-locking composition so we have the hypotheses:
+	\begin{gather}
+		V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash R_{23}\mpar{s_2, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{5} \\
+		V_{21} \uplus \biguplus_\subbox{t_{12} \in \fOT{s_{12}}} \fvars{t_{12}} \vdash \reach{A_{21}}\mpar{s_{21}} \wedge \bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}} \implies \bigvee_\subbox{t_{21} \in \fOT{s_{21}}} \fguard{t_{21}} \hyp{6}
+	\end{gather}
+	We use \hyp{5} with valuation \(\sigma\) to get \nmm{\nu: \biguplus_\subbox{t_{12} \in \fOT{s_{12}}} \fvars{t_{12}} \to \values}.
+	The left side of the implication is proved using \hyp{4a} and \hyp{4c} because the guards from transitions of \(A_3\) are still in transitions of \(A_{31}\), the right side gives:
+	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{5'} \]
+	We then use \hyp{6} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t_{21} \in \fOT{s_{21}}} \fvars{t_{21}}}.
+	The left side of the implication is proved using \hyp{4b} and \hyp{5'}, the right side gives:
+	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t_{21} \in \fOT{s_{21}}} \fguard{t_{21}} \hyp{6'} \]
+	\goal{1} is proved for valuation \(\nu'\) by admitting the left side and using \hyp{6'}.
+\end{proof}
 

### 2021-06-14 2021-Refinement/report.tex
comments on intro

--- 2021-06-12 2021-Refinement/report.tex
@@
 \usepackage{fontspec}
-\usepackage[hmargin=3cm]{geometry}
+\usepackage[hmargin=0.5in,marginparwidth=1.5in,includemp]{geometry}
 \usepackage{amsmath}
@@
 \section{Introduction}
-The open automata model is used to give the semantic of open pNets \cite{2007.10770}.
+The open automata model was originally designed to give the semantic of open pNets \cite{2007.10770}.
 Open pNets are not petri nets but an intermediate representation used in the VerCors project to perform verification \cite{henrio:01252323}.
  Verification is the process of checking that an implementation satisfies a specification.
-Open pNets with the open automaton semantics and equivalence relation introduced in previous work \cite{2007.10770} were sucessfully used to model and verify BIP and GCM \cite{qin:01823507, ameurboulifa:01526055}.
-However equivalences relations are not always sufficient to perform verification, refinement relations are also used.
-For instance an example of open pNet where equivalence is not sufficient was encountered in an article about algorithms fo weak bisimulation on open automata \cite{wang:03126313}.
-
-The contributions of this article are the definition of composition for open automata without having to define open pNets, and the introduciton of several refinement relations for open automata.
-% TODO: expand
+\Ludo{verification is more general than that (or you need to refine specification): checking typing or absence of deadlocks belong to verification}
+Open pNets with the open automaton semantics and equivalence relation introduced in previous work \cite{2007.10770} were sucessfully used to model and verify some properties of applications based on BIP  and GCM \cite{qin:01823507, ameurboulifa:01526055} \Ludo{cite and expand acronym (x2)}.
+However equivalence relations are not always sufficient to perform verification, refinement relations are also used. \Ludo{verification/refinement/equivalence needs to be refined and explained}
+For instance a usecase where open pNet where equivalence is not sufficient can be found  in an article about algorithms fo weak bisimulation on open automata \cite{wang:03126313}.
+
+\Ludo{choose: either 1) you do not refer to open pnets below and explain informally open automata here (why are they useful, what makes them different from automata), or 2) you want to refer to pnets in the following and you explain informally pnets, uatomata and the relation}
+
+The contributions of this article \Ludo{report?} are the definition of composition for open automata without having to define open pNets, and the introduction of several refinement relations for open automata\marginpar{TODO: expand}.
 
 % Related work: thesis
+
+\Ludo{RAPPEL: pour ecrire une intro: 1) on ecrit les contribs, 2) on explique avant les termeis techniques pour que le lecteur comprenne les contribs, 3) quand on a quasi fini le reste on ecrit le plan.
+ON peut commencer 1 et 2 un peu tot meme si il faut rediger le tout assez tard: on peut pas ecrire proprement un article sans avoir en tete les contribs de celui ci}
 
@@
 In Section \ref{sec:def} we give a clean and up to date definition of open automata.
-In Section \ref{sec:comp} we define their composition without requiring the use of open pNets.
-In Section \ref{sec:proofelts} we adapt the standard properties related to refinement relation from LTS to open automata.
-After that Section \ref{sec:prelref} is dedicated to progressively build a refinement relation.
+In Section \ref{sec:comp} we define their composition without requiring the use of open pNets \Ludo{does this mean that previous definitions were using open pnets?
+this might be clarified in contributions but when you redo a definition you must highlight why a new definition was necessary}.
+In Section \ref{sec:proofelts} we adapt several standard properties that we use in the definition of refinement relation from LTS to open automata.
+After that Section \ref{sec:prelref} is dedicated to progressively build a refinement relation and explain the elements of this construction.
 Section \ref{sec:refinement} introduces and analyses the refinement relation on open automata.
@@
 However \(\mbrc{\alpha \mapsto 1, \beta \mapsto 2, \gamma \mapsto 3}\) has no generating expression and is represented here with the finite version of first notation.
-
-The disjoint union on set is noted \(\uplus\).
-There are several ways of ensuring a union is disjoint, we will indifferently either suppose sets are disjoint or rename conflicting object (useful for variables).
 The disjoint union of two maps \(\varphi: I \to X\) and \(\psi: J \to Y\) with \(I \cap J = \emptyset\) is \(\varphi \uplus \psi: I \uplus J \to X \cup Y\).
@@
 
-The terms \(\terms\) is a term algebra.
+The terms \(\terms\) is a term algebra\marginpar{reference to come}.
 As any term algebra it has constant symbols with arity, variables, and a typing mechanism to distinguish well-formed and ill-formed terms.
@@
 \begin{defi}[Relation on configurations]
-A relation on configurations of \(\OAg[1]\) and \(\OAg[2]\) is a function \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
+A relation on configurations of two open automata \(\OAg[1]\) and \(\OAg[2]\) is a function \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
 
@@
 The important properties we consider for the relation on states are being a simulation and the prevention of deadlocks as defined in the following definitions.
-\begin{defi}[Pre-simulation]
-Let \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\).
-A relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a pre-simulation if it satisfies both
+\begin{defi}[Pre-simulation]\label{def:presim}
+For two open automata \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\), a relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a pre-simulation if it satisfies both
 \defitem Initial configurations are related: \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\);
@@
 \end{defi}
-This definition translated to open automata the classical definition of simulation \cite{10.1007/3-540-54430-5_78}.
+This definition translated to open automata the classical definition of simulation \marginpar{cite: Fernandez-Mounier-91-b}.
 The last formula means that for every pair of related configurations of the automaton and every possible transitions (\(\vdash g_1\)) from the first automaton, there is a possible transition (\(\vdash g_2\)) such that the produced action matches (\(\alpha_1 = \alpha_2\)), the same holes' action (\(J'_1 \cap J'_2\)) matches (\(\beta_{1j} = \beta_{2j}\)) and the target states are related after variable update.
@@
 Here we assume that one of the related open automata can be obtained by composing an open automaton in a hole, open automaton which can have holes itself.
-This implies that there is no relation between their holes, for instance composing \(A_i\) in \(j_i\) (\(1 \leq i \leq n\)) of \(A_0\) gives the set of holes \(J \defobject \mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}\) that is neither subset nor superset of \(J_0\).
+This implies that there is no relation between their holes, for instance composing \(A_i\) in \(j_i\) (\(1 \leq i \leq n\)) of \(A_0\) gives the set of holes \nmm{J \defobject \mpar{\biguplus_\subbox{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}} that is neither subset nor superset of \(J_0\).
 Yet we still assume that in holes with the same name, the same open automaton will be composed.
@@
 \begin{defi}[Non-locking composition, intuitive definition]
-Let \(A_i \defobject \OAg[i], 0 \leq i \leq n\).
-The composition \(A \defobject A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is non-locking if \(A\) has a reachability predicate satisfying:
-From reachable configurations, if there was a possible transition in \(A_0\) then there is a possible transition in \(A\).
+Let \(A_c \defobject \OAg[c]\), \(A_p \defobject \OAg[p]\) and \(j \in J_p\).
+The composition \(A \defobject A_p\subst{A_c}{j}\) is non-locking if \(A\) has a reachability predicate satisfying:
+From reachable configurations, if there was a possible transition in \(A_p\) then there is a possible transition in \(A_p\subst{A_c}{j}\).
 
@@
 \begin{multline*}
-	\forall s \defobject \mpar{s_0, s'} \in S_0 \times \prod_\subbox{1 \leq i \leq n} S_i, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A}\mpar{s}} \implies \\
-	\mpar{\exists t_0 \in \fOT{s_0}, \exists \nu_0: \fvars{t_0} \to \values, \sigma \uplus \nu_0 \vdash \fguard{t_0}} \implies \\
+	\forall s \defobject \mpar{s_p, s_c} \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A_p\subst{A_c}{j}}\mpar{s}} \implies \\
+	\mpar{\exists t_p \in \fOT{s_p}, \exists \nu_p: \fvars{t_p} \to \values, \sigma \uplus \nu_p \vdash \fguard{t_p}} \implies \\
 	\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t}
@@
 \end{defi}
-We can expand the alias \(V\) into \nmm{\biguplus_\subbox{1 \leq i \leq n} V_i \uplus V_0} and transform the last transition \(t\) into a pair \(\mpar{t, t_0}\) where the second transition is the one from \(A_0\) which generated \(t\).
+We can expand the aliases \(S, V\) into \(S_p \times S_c, V_p \uplus V_c\) and transform the last transition \(t\) into a pair \(\mpar{t_p, t}\) where the first transition is the one from \(A_p\) which generated \(t\).
 Doing that makes the definition become mildly similar with the deadlock prevention one. % OR slightly
@@
 \begin{defi}[Non-locking composition, working definition]
-\(A \defobject A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is a non-locking composition if:
-\[ \forall s \defobject \mpar{s_0, s'} \in S, V \uplus \biguplus_\subbox{t_0 \in \fOT{s_0}} \fvars{t_0} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_0 \in \fOT{s_0}} \fguard{t_0} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
+The composition \(A \defobject A_p\subst{A_c}{j}\) is a non-locking composition if:
+\[ \forall s \defobject \mpar{s_p, s_c} \in S, V \uplus \biguplus_\subbox{t_p \in \fOT{s_p}} \fvars{t_p} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
 \end{defi}
@@
 
-This new definition of composition can replace the standard composition.
-For the simultaneous composition, we may think that if the last composition of a specific composition order is non-locking, then every composition is non-locking for all composition orders.
+This new definition of composition can replace the standard composition in the case where only one hole is filled, and also be extended to a simultaneous composition.
+For the simultaneous composition, we may think that if the last composition of a specific composition order is non-locking, then every composition is non-locking for all composition order. % orderS
 Unfortunately it is not true.
@@
 For two open automata \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\triangle\) simulation of \(A_1\) by \(A_2\) if:
-\item[1)] \(J_1 \triangle J_2\)
-\item[2)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
-\item[3)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)\vspace{-8pt}
+\defitem \(J_1 \triangle J_2\)
+\defitem \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
+\defitem \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)\vspace{-8pt}
 \noindent\begin{multline*}
@@
 \begin{thm} The hole-\(\triangle\) simulation on automata is a preorder. \end{thm}
-The idea for reflexivity is that the related automata are always in the same configuration.
-\[ R \defobject \mpar{s, s'} \mapsto \choice{\bigwedge_{v \in V} v_1 = v_2 & \text{if } s = s'\\ \bot & \text{otherwise}} \]
-Where \(v_x\) is the renaming to distinguish conflicting automaton variables.
-\(R\) is a witness of the reflexivity, the proof is mainly the same as several of the following ones so it will be omitted.
-
-Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\).
-Let \(R_{12}\) be a hole-\(\triangle\) simulation of \(A_1\) by \(A_2\) and \(R_{23}\) of \(A_2\) by \(A_3\), we want to define \(R\) by saying that there exists a state \(s_2 \in S_2\) and values for \(V_2\) such that \(R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}\).
+% TODO: give intuition, then define R on one line then renamin on the line after
+Reflexivity is immediate with \(R \defobject \mpar{s, s'} \mapsto \choice{\bigwedge_{v \in V} v_1 = v_2 & \text{if } s = s'\\ \bot & \text{otherwise}}\) where \(v_x\) is the renaming to distinguish conflicting automaton variables.
+
+For three open automata \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\), such that \(R_{12}\) is a hole-\(\triangle\) simulation of \(A_1\) by \(A_2\) and \(R_{23}\) of \(A_2\) by \(A_3\), we want to define \(R_{13}\) by saying that there exists a state \(s_2 \in S_2\) and values for \(V_2\) such that \(R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}\).
 However we cannot talk about states in formulas.
 The solution is to expand the existential quantifier on states as we did in deadlock prevention, which is possible because states are finite.
-\[ R \defobject \mpar{s_1, s_3} \mapsto \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \]
-\(R\) is a witness of the transitivity, proof is given in Appendix \ref{apx:trans}.
+\nmm{R_{13} \defobject \mpar{s_1, s_3} \mapsto \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}} is a witness of the transitivity, proof is given in Appendix \ref{apx:trans}.
+\begin{thm}[Context refinement] Hole-equal simulation is context refining. \end{thm}
+For three open automata \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) with \(J_1 = J_2\), let \(k \in J_1\).
+Let \(R_{12}\) be a hole-equal simulation of \(A_1\) by \(A_2\) and \(\reach{A\subst{A_3}{k}}\) be a witness that \(A\subst{A_3}{k}\) is non-locking.
+The idea for the relation on configurations is that \(A_2\) simulates \(A_1\) while \(A_3\) does the same things in both compositions in the hole \(k\).
+\[ R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \]
+Where \(y_{3x}\) is the renaming of \(y_3\) from \(A_3\) in \(A_x\subst{A_3}{k}\).
 \begin{prop}[Limited composition correctness]\label{prop:cc'} Hole-subset simulation is correct w.r.t.\@ composition with automata without holes. \end{prop}
-For two open automata \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\) with \(J_2 = \emptyset\), let \(k \in J_1\) and \(A \defobject A_1\subst{A_2}{k}\).
+For two open automata \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\) with \(J_2 = \emptyset\), let \(k \in J_1\) and \(A \defobject A_1\subst{A_2}{k}\), with \(A = \OAg\).
 Let \(\reach{A}\) be a witness that \(A\) is non-locking.
@@
 Where \(y_{1'}\) is the renaming of \(y_1\) from \(A_1\) in \(A\).
-\(R\) is a witness of the limited composition correctness, proof is given in Appendix \ref{apx:lchs}.
 \begin{prop}[Special composition correctness]
-For three open automata \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3\), let \(k \in J_1 \setminus J_2\) and \(R_{12}\) be a hole-superset simulation of \(A_1\) by \(A_2\).
-There is a hole-superset simulation of \(A_1\subst{A_3}{k}\) by \(A_2\).
+Let \(A_1 \defobject \OAg[1]\) be hole-superset simulated by \(A_2 \defobject \OAg[2]\).
+Let \(j \in J_1 \setminus J_2\) and \(A_3\) an open automaton.
+There is a hole-superset simulation of \(A_1\subst{A_3}{j}\) by \(A_2\).
 \end{prop}
-Let \(\reach{A_1\subst{A_3}{k}}\) be a witness that \(A_1\subst{A_3}{k}\) is non-locking.
-The idea for the relation on configurations is to combine the non-locking composition and the already existing realtion on configurations.
-\[ R \defobject \mpar{\mpar{s_1, s_3}, s_2} \mapsto R_{12}\mpar{s_1, s_2} \wedge \reach{A_1\subst{A_3}{k}}\mpar{s_1, s_3} \]
-\(R\) is a witness of the secial composition correctness, proof is given in Appendix \ref{apx:schs}.
-
-For composition correctness, the hole-subset simulation can only tell if there is a refinement when the composed automata have no holes.
-To lift this limitation we need to allow adding holes which doesn't have a direct interpretation.
-At first a solution using a function mapping the action performed by the new holes in the composition to the ones performed by removed hole in the base automaton was explored.
-It was abandonned because the base automaton has nothing intelligent to tell about the action required by the composed automata.
-That is the reason the hole-superset simulation doesn't constrain the action performed by the added holes.
-
-Only one of the hole-\(\triangle\) simulations cannot tell that a non-locking composition with any automaton is a refinement because we need at the same time to add and remove holes, hence the need of the special composition correctness for hole-superset.
-ALso an issue arises when trying to tell that a composition is a refinement of the base automaton: the refinement relation cannot compare the holes sets.
-This conflicts with the transitivity propriety when a hole present in both extrema of the chain is absent in an intermediate automaton.
-In that case all the constraint on holes actions are lifted even if we would like to require an equality of these actions on the transitive cloture.
-
+Proofs of the above theorem and propositions are given in Appendix \ref{apx:ophts}.
+
+% J'2 \subseteq J'1 in hole-subset, J'1 \subseteq J'2 in hole-superset (decide of transition variable with holes); composition with new holes is hole-subset where hole variables are free then hole-superset where hole names have no conflicts with removed holes.
+Transitivity must ensure holes name have no conflict for that reason!
+
+% Mettre des sets de noms en commun qu'on veut effectivement mapper pour la transitivité
+% Explain what happens on holes constraints and action constraints
+% refinement can be used to specify behaviour/constraints on holes (like an API: first do anything not involving the api, then initialise the api, then do whatever you want that do not unload the api, then unload the api by returning to the first state), then have a relation for every hole with a different automata and this means well behaving with respect to the environement (holes)
 \section{Refinement relation for open automata}\label{sec:refinement}
-One of the solutions to keep transitivity and constraints on holes actions from same holes is to keep track of which holes are in common at each step of refinement.
-The transitive refinement will have to either rename the holes without constraints or explicitly say which holes have constraints.
 \begin{defi}[Open automata refinement]
@@
 \end{multline*}
-Giving \(R\) and \(H\) is sufficient to characterise the refinement, so we call \(\mpar{R, H}\) a hole-tracking simulation of \(A_1\) by \(A_2\).
-\end{defi}
-It is basically the same definition as the refinement relation deduced from hole-\(\triangle\) simulations.
-\(R\) is a kind of hole-\(\triangle\) simulation but without the \(\triangle\) constraint on hole sets.
-On top of that every actions of the holes outside \(H\) is unconstrained in the related automata.
-
-The transitivity property becomes \(\wrel{X}{A}{B} \wedge \wrel{Y}{B}{C} \implies \wrel{X \cap Y}{A}{C}\).
-It behaves the same as if the holes outside the intersection were renamed to avoid conflicts in the first place.
-This makes the comination of the transitivity proofs of hole-\(\triangle\) simulation sufficient to prove transitivity.
-
-Not renaming conflicting holes still have an interest.
-If we are trying to build an automaton \(A\) with several constraints \(A \leq B_i, i \in I\) -method B like- and each \(B_i\) is a refinement of some automaton \(C\) then we can have each \(B_i\) constrain a different subset of \(A\)'s holes.
-On each individual path \(A \leq B_i \leq C\), some holes of \(A\) are unconstrained but when considering all path they are all constrained.
-
-The other interesting properties left to check are correctness w.r.t.\@ composition, context refinement, composition congruence and compatibility with FH-bisimulation.
-Proving them for the open automata refinement will also prove them for each hole-\(\triangle\) simulation as they are just restricted cases.
-% TODO: Explain two refinement steps comositions so that Correctness wrt composition is trivial
-\begin{thm}[Context refinement] Open automata refinement is context refining. \end{thm}
-Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\).
-Let \(k \in J_1 \cap J_2\), \(\mpar{R_{12}, H_{12}}\) be a hole-tracking simulation of \(A_1\) by \(A_2\) and \(\reach{A\subst{A_3}{k}}\) be a witness that \(A\subst{A_3}{k}\) is non-locking.
-The idea for the relation on configurations is that \(A_2\) simulates \(A_1\) while \(A_3\) does the same things in both compositions in the hole \(k\).
-\begin{gather*}
-	R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \\
-	H \defobject J_3 \uplus H_{12} \setminus \mbrc{k}
-\end{gather*}
-Where \(y_{3x}\) is the renaming of \(y_3\) from \(A_3\) in \(A_x\subst{A_3}{k}\).
-\(\mpar{R, H}\) is a witness of \(\wrel{H}{A_{13}}{A_{23}}\), proof is given in Appendix \ref{apx:cr}.
-% TODO: Proof for Congruence \ref{apx:cong}
-% TODO: Proof for FH-bisimulation compatibility \ref{apx:FHbcomp}
-
-% TODO: What happens on untracked holes (untracked holes equivalent behaviour => free variables; some sort of daisy equivalence)
+\end{defi}
+% refinement relation definition
+% Explain definition, really needed
+% safety is no longer trivial, prove the safety
+% Prove all expected properties except pre-simulation
+
+% What happens on untracked holes (untracked holes equivalent behaviour => free variables; some sort of daisy equivalence)
+% Yet having untracked holes is interesting because we can be a refinement of several OA, each on different holes.
+
+\section{Future work}
+% TODO: Weak variants, tau-stuttering, livelocks
+% Other kind of refinement relation that \Quentin{I may explore}{This is a note for possible path, some may be explored, some may not.} are control refinement/hole refinement\footnote{No good formulation atm, the idea is that \(a \leq b \defnotation sth \wedge J_a \setminus J_b \leq_{ctrl} J_b \setminus J_a\), sth is probably a clause to ensure that they behave the same without holes involved.}, (meet semi)lattice refinement\footnote{meet = handshake, \(a \leq b \defnotation a = a || b\) with sync holes, I think this will be equivalent to hole-identical sim, (join=non-det choice?)}, weak-simulation refinement\footnote{Weak variation for each interesting simulation refinement}, composition-correct refinement\footnote{Basically a stricter variant of simulation-refinement where simulation has to take place the other way for some transitions (no different holes?) in order to be correct wrt composition}.
 
 \section{Conclusion}
-% TODO: recap contribs?
-
-The refinement presented here still do not work on the motivating example because of silent actions.
-To be able to refine in the presence of silent action, a weak variant of the simulation is needed.
-This variant will also probably be able to encompass action refinement as a valid refinement because the mechanism are similar.
 
@@
 \begin{exi}[Deadlocks introduced by composition]
+\Ludo{TODOludo}{lire l'explication}
 This example reuses the counter introduced in Figure \ref{fig:tlh}.
@@
 	However we cannot yet prove it because we don't know whether \(t_2\) and \(t_1\) match.
-	In order to get a \(t_2\) matching \(t_1\) we will use the fact that \(R\) is a pre-simulation:
+	In order to get a \(t_2\) matching \(t_1\) we will use the fact that \(R\) is a \hyperref[def:presim]{pre-simulation}:
 	\begin{multline}
@@
 
-\section{Proofs of properties for hole-\(\triangle\) simulation}
+\section{Proofs of properties for hole-\(\triangle\) simulation}\label{apx:ophts}
 
@@
 \[ \sigma \uplus \nu \vdash \alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \wedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \hyp{4} \]
-We have \(J'_{2x} \cap J_1 = J'_{2x} \cap J'_1\) in \hyp{4}:
-\begin{align*}
-	J'_{2x} \cap J_1 & \subseteq J'_{2x} \tag{1} \\
-	J'_{2x} \cap J_1 & = J'_1 \cap J_2 & \text{by \hyp{2}} \\
-	& \subseteq J'_1 \tag{2} \\
-	J'_{2x} \cap J_1 & \subseteq J'_{2x} \cap J'_1 & \text{by (1) and (2)} \tag{3} \\
-	J'_{2x} \cap J'_1 & \subseteq J'_{2x} \cap J_1 & \text{by } J'_1 \subseteq J_1 \tag{4} \\
-	J'_{2x} \cap J_1 & = J'_{2x} \cap J'_1 & \text{by (3) and (4)}
-\end{align*}
-So we can prove \goal{0'} for the transition \(t_{2x}\) and the valuation \(\nu\) using \hyp{4}.
+% TODO: put that on several lines using a math env
+We have \(J'_{2x} \cap J_1 \subseteq J'_{2x}\) and by \hyp{2}, \(J'_{2x} \cap J_1 = J'_1 \cap J_2 \subseteq J'_1\) so \(J'_{2x} \cap J_1 \subseteq J'_{2x} \cap J'_1\).
+Also \(J'_{2x} \cap J'_1 \subseteq J'_{2x} \cap J_1\) because \(J'_1 \subseteq J_1\) by definition of an open transition.
+Hence \(J'_{2x} \cap J_1 = J'_{2x} \cap J'_1\) in \hyp{4}.
+We can get back to prove \goal{0'} with the transition \(t_{2x}\) and the valuation \(\nu\) by \hyp{4}.
 \end{proof}
 
-\subsection{Limited composition correctness for hole-subset simulation}\label{apx:lchs}
+\subsection{Context refinement for hole-equal simulation}
+Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) be three pen automata.
+Let \(k \in J_1\), \(A_{13} \defobject A_1\subst{A_3}{k}\) and \(A_{23} \defobject A_2\subst{A_3}{k}\) with \(A_{13} = \OAg[13]\) and \(A_{23} = \OAg[23]\).
+Let \(R_{12}\) be a hole-equal simulation of \(A_1\) by \(A_2\) and \(\reach{A_{13}}\) be a witness that \(A_{13}\) is non-locking.
+\[ R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \]
+Where \(y_{3x}\) is the renaming of \(y_3\) from \(A_3\) in \(A_{x3}\).
+We want to prove that \(R\) is a hole-equal simulation of \(A_{12}\) by \(A_{23}\).
+\begin{proof}
+\defitem \(J_{13} = J_3 \cup J_1 \setminus \mbrc{k} = J_3 \cup J_2 \setminus \mbrc{k} = J_{23}\) by \(J_1 = J_2\).
+\defitem For \(\sigma_{013} \uplus \sigma_{023} \vdash R\mpar{s_{013}, s_{023}}\) we use the fact that \(R_{12}\) relates inital configurations and initial configuration is reachable:
+	\begin{align*}
+		& \sigma_{013} \uplus \sigma_{023} \vdash R\mpar{s_{013}, s_{023}} \\
+		\iff & R\mpar{\mpar{s_{01}, s_{031}}, \mpar{s_{02}, s_{031}}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{031} \uplus \sigma_{032}} \\
+		\iff & R_{12}\mpar{s_{01}, s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}\psubst{\sigma_{013}} \wedge \mpar{\bigwedge_{v_3 \in V_3} v_{31} = v_{32}}\psubst{\sigma_{031} \uplus \sigma_{032}} \\
+		\iff & \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}} \wedge \bigwedge_\subbox{v_3 \in V_3} \sigma_{031}\mpar{v_{31}} = \sigma_{032}\mpar{v_{32}} \\
+		\iff & \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}} \wedge \top
+	\end{align*}
+\defitem Let \(s_{13} \defobject \mpar{s_1, s_{31}} \in S_{13}\) and \(s_{23} \defobject \mpar{s_2, s_{32}} \in S_{23}\).
+	We want to prove both
+	\begin{align*}
+		& \bigsymb{\forall} t_{13} \defobject \OTx{13}{}{13}{13} \in \fOT{s_{13}}, \bigsymb{\exists} \mpar{t_{23x} \defobject \OTx{23}{x}{23x}{23x} \in \fOT{s_{23}}}^{x \in X}, \\
+		& \quad \mpar{\forall x \in X, J'_{23x} \cap J_{13} = J'_{13} \cap J_{23}} \\[-10pt]
+		& \nwedge V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \Rightarrow \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\!\!\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \\[12pt]
+			\nwedge g_{23x} \wedge R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
+		\end{array}\!\!} \goal{0}
+	\end{align*}
+	\[ V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash R\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \goal{1} \]
+	Let \nmm{t_{13} \defobject \OTx{13}{}{13}{13} \in \fOT{s_{13}}}, we use the fact that \(R_{12}\) is a simulation from the states \(\mpar{s_1, s_2}\) to get the hypothesis:
+	\begin{align*}
+		& \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
+		& \quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
+		& \nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
+			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}} \hyp{1}
+	\end{align*}
+	Transition \(t_{13}\) is obtained in \(A_{13}\) by composition of two transitions \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}} and \nmm{t_{31} \defobject \OTx{31}{}{31}{31} \in \fOT{s_{31}}} if \(k \in J'_1\) or by a the first transition and a fixed state \(s_{31}\) if \(k \notin J'_1\).
+	We use \hyp{1} with the transition \(t_1\) to get
+	\begin{gather*}
+		\mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X} \\
+		\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2 \hyp{1'} \\
+		V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
+			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}} \hyp{1"}
+	\end{gather*}
+	To build the family of transitions we need to know if \(k \in J'_{2x}\) for a every \(x \in X\):
+	\begin{align*}
+		J'_1 & = J'_1 \cap J_1 \\
+		& = J'_1 \cap J_2 & \text{by } J_1 = J_2 \\
+		& = J'_{2x} \cap J_1 & \text{by \hyp{1'}} \\
+		& = J'_{2x} \cap J_2 & \text{by } J_1 = J_2 \\
+		& = J'_{2x} \hyp{2}
+	\end{align*}
+	In the case \(s_{31} \neq s_{32}\) we can give the empty family, it won't cause any issue.
+	Otherwise \(s_{31} = s_{32}\) so we can copy \(t_{31}\) into \nmm{t_{32} = \OTx{32}{}{32}{32}} to avoid conflicts.
+	We also name \(t_3\) the original transition from \(T_3\).
+	Using \hyp{2} we can build the familly of transition generated by the family \(t_{2x}^{x \in X}\):
+	\[ t_{23x}^{x \in X} \defobject x \mapsto \choice{
+		\OT{\mpar{s_2, s_{32}}}{\mpar{s'_{2x}, s'_{32}}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x} \setminus \mbrc{k}} \uplus \beta_{3j}^{j \in J'_{32}}}{g_{2x} \wedge g_{32} \wedge \alpha_{32} = \beta_{2xk}}{\psi_{2x} \uplus \psi_{32}} & \text{if } k \in J'_{2x} \\
+		\OT{\mpar{s_2, s_{32}}}{\mpar{s'_{2x}, s_{32}}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_2}}{g_2}{\psi_2} & \text{otherwise}
+	} \label{eq:t23x} \]
+	We will prove \goal{0} for the family \(t_{23x}^{x \in X}\), the new goals are
+	\begin{gather}
+		\forall x \in X, J'_{23x} \cap J_{13} = J'_{13} \cap J_{23} \goal{0'} \\
+		V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \\[12pt]
+			\nwedge g_{23x} \wedge R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
+		\end{array}} \goal{2}
+	\end{gather}
+\item[\goal{0'}:] Let \(x \in X\), by case on \(k \in J'_1\):
+	\begin{align*}
+		\text{If } k \in J'_1: && J'_{23x} \cap J_{13} & = \mpar{J'_{31} \cup J'_{2x} \setminus \mbrc{k}} \cap \mpar{J_3 \cup J_1 \setminus \mbrc{k}} \\
+		&&& = \mpar{J'_{31} \cap J_3} \cup \mpar{J'_{2x} \cap J_1} \setminus \mbrc{k} \\
+		&&& = \mpar{J'_{31} \cap J_3} \cup \mpar{J'_1 \cap J_2} \setminus \mbrc{k} & \text{by \hyp{1'}} \\
+		&&& = \mpar{J'_{31} \cup J'_1 \setminus \mbrc{k}} \cap \mpar{J_3 \cup J_2 \setminus \mbrc{k}} \\
+		&&& = J'_{13} \cap J_{23} \\
+		\text{If } k \notin J'_1: && J'_{23x} \cap J_{13} & = \mpar{J'_{2x} \setminus \mbrc{k}} \cap \mpar{J_1 \setminus \mbrc{k}} \\
+		&&& = J'_{2x} \cap J_1 & \text{by } k \notin J'_1 = J'_{2x} \text{ \hyp{2}} \\
+		&&& = J'_1 \cap J_2 & \text{by \hyp{1'}} \\
+		&&& = \mpar{J'_1 \setminus \mbrc{k}} \cap \mpar{J_2 \setminus \mbrc{k}} & \text{by } k \notin J'_1 \\
+		&&& = J'_{13} \cap J_{23}
+	\end{align*}
+\item[\goal{2}:] Let \(\sigma: V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \to \values\).
+	We use dummy values for the variables in \nmm{\biguplus_{x \in X} \fvars{t_{23x}}} to get the left side of the implication as an hypothesis (independant from these values):
+	\[ \sigma \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \hyp{3} \]
+	If \(s_{31} \neq s_{32}\) then this hypothesis is \(\sigma \vdash \bot\), the empty family works and the proof is finished.
+	We can assume \(s_{31} = s_{32}\) and the family given \hyperref[eq:t23x]{previously} works.
+	We break \hyp{3} into
+	\begin{gather}
+		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{3a} \\
+		\sigma \vdash \reach{A_{13}}\mpar{s_{13}} \hyp{3b} \\
+		\sigma \vdash \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} \hyp{3c} \\
+		\sigma \vdash g_{13} \hyp{3d}
+	\end{gather}
+	We use \hyp{1"} with valuation \(\sigma\) on variables \(V_1 \uplus V_2 \uplus \fvars{t_1}\), which is possible because the composition of transitions doesn't remove any variable (the simplification steps do, they give bisimilar automata).
+	Then we get the values of the implicit \(\exists\) in \nmm{\nu: \biguplus_{x \in X} \fvars{t_{2x}}}.
+	The left side of the implication is proved with \hyp{3a} and \hyp{3d}.
+	So we get a \(x \in X\) such that
+	\begin{gather}
+		\sigma \uplus \nu \vdash \alpha_1 = \alpha_{2x} \hyp{4a} \\
+		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \hyp{4b} \\
+		\sigma \uplus \nu \vdash g_{2x} \hyp{4c} \\
+		\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \hyp{4d}
+	\end{gather}
+	If \(k \in J'_1\), we extend the valuation \(\nu\) to cover the variables of \(t_3\) in \(t_{23x}\) using their value in \(t_{13}\), \(\nu' \defobject \nu \uplus \mset{v_{32} \mapsto \sigma\mpar{v_{31}}}{v_3 \in \fvars{t_3}}\)
+	Otherwise \(\nu' \defobject \nu\).
+	We progress on \goal{2} by giving the valuation \(\sigma \uplus \nu'\) to the implicit \(\exists\), admitting the left side of the implication and choosing to prove the branch \(x\) of the disjunction:
+	\begin{gather}
+		\sigma \uplus \nu' \vdash \alpha_{13} = \alpha_{23x} \goal{3a} \\
+		\sigma \uplus \nu' \vdash \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \goal{3b} \\
+		\sigma \uplus \nu' \vdash g_{23x} \goal{3c} \\
+		\sigma \uplus \nu' \vdash R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}} \goal{3d}
+	\end{gather}
+	Because composition doesn't change the produced actions nor its variables, \goal{3a} is proved by \hyp{4a}.
+	\goal{3b} holds because the valuations for the actions of the holes in \(J_3\) coincide by definition of \(\nu'\) and by \hyp{4b} for the others.
+	For \goal{3c} we have two cases, if \(k \notin J'_1\) then \(g_{23x} \equiv g_{2x}\) and \hyp{4c} is sufficient, if \(k \in J'_1\) then \(g_{23x} \equiv g_{2x} \wedge g_3 \wedge \alpha_3 = \beta_{2xk}\) so we also need \hyp{3d} (\(g_{13} \equiv g_1 \wedge g_3 \wedge \alpha_3 = \beta_{1k}\)) and \hyp{4b} for the value \(k\) (\(\beta_{1k} = \beta_{2xk}\)).
+	\goal{3d} is proved using \hyp{4d}, \hyp{3b} with the preservation of reachability across transitions (+ \hyp{3d}), \hyp{3c} and the fact that \(A_3\) performs the same transition with same values in both composed automata:
+	\begin{align*}
+		& \sigma \uplus \nu' \vdash R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}} \\
+		\iff & \sigma \uplus \nu' \vdash \mpar{R_{12}\mpar{s'_1, s'_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32}}\psubst{\psi_1 \uplus \psi_{31} \uplus \psi_{2x} \uplus \psi_{32}} \\
+		\iff & \sigma \uplus \nu' \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}} \wedge \bigwedge_\subbox{v_3 \in V_3} \psi_{31}\mpar{v_{31}} = \psi_{32}\mpar{v_{32}} \\
+		\iff & \sigma \uplus \nu' \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}} \wedge \bigwedge_\subbox{v_3 \in V_3 \cup \fvars{t_3}} v_{31} = v_{32} \\
+		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \reach{A_{13}}\mpar{s'_{13}}\psi_{13}} \wedge \mpar{\sigma \vdash \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32}}
+	\end{align*}
+\item[\goal{1}:] Let \nmm{\sigma: V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \to \values}.
+	We use dummy values for the variables in \nmm{\biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}}} to get the left side of the implication (independant from dummy values), immediately broken into
+	\begin{gather}
+		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{5a} \\
+		\sigma \vdash \reach{A_{13}}\mpar{s_{13}} \hyp{5b} \\
+		\sigma \vdash \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \hyp{5c}
+	\end{gather}
+	\(R_{12}\) is a simulation and \(\reach{A_{13}}\) witnesses the non-locking simulation so we have the hypothesis:
+	\begin{gather}
+		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6} \\
+		V_{13} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A_{13}}\mpar{s} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{7}
+	\end{gather}
+	We use \hyp{6} with valuation \(\sigma\) projected on the variables from generating transitions in \(A_2\) to get \nmm{\nu: \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
+	The left side of the implication is proved using \hyp{5a} and \hyp{5c} because the guards from transitions of \(A_2\) are still in transitions of \(A_{23}\), the right side gives:
+	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6'} \]
+	We then use \hyp{7} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}}}.
+	The left side of the implication is proved using \hyp{5b} and \hyp{6'}, the right side gives:
+	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{7'} \]
+	\goal{1} is proved for valuation \(\nu'\) by admitting the left side and using \hyp{7'}.
+\end{proof}
+
+\subsection{Limited composition correctness for hole-subset simulation}
 Let \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\) be open automata, where \(J_2 = \emptyset\).
@@
 Where \(y_{1'}\) is the renaming of \(y_1\) from \(A_1\) in \(A\).
-We want to prove that \(R\) is a hole-subset simulation of \(A\) by \(A_1\).
+We want to prove that \(R\) is a hole-subset simulation of \(A\) by \(A_1\):
 \begin{proof}
-\item[1)] \(J = J_2 \uplus J_1 \setminus \mbrc{k} = \emptyset \uplus J_1 \setminus \mbrc{k} \subseteq J_1\)
-\item[2)] We use the fact that \(R\) doesn't constrain the behaviour of \(J_2\) and initial configuration is reachable:
-	\begin{align*}
-		\sigma_0 \uplus \sigma_{01} \vdash R\mpar{s_0, s_{01}} \iff & \mpar{\reach{A}\mpar{s_0} \wedge \bigwedge_{v_1 \in V_1} v_{1'} = v_1}\psubst{\sigma_{01'} \uplus \sigma_{02} \uplus \sigma_{01}} \\
-		\iff & \reach{A}\mpar{s_0}\psubst{\sigma_0} \wedge \bigwedge_\subbox{v_1 \in V_1} \sigma_{01'}\mpar{v_{1'}} = \sigma_{01}\mpar{v_1} \\
-		\iff & \sigma_0 \vdash \reach{A}\mpar{s_0}
-	\end{align*}
-\item[3)] Let \(s \defobject \mpar{s_{1'}, s_2} \in S\) and \(s_1 \in S_1\).
+\defitem \(J = J_2 \cup J_1 \setminus \mbrc{k} = \emptyset \cup J_1 \setminus \mbrc{k} \subseteq J_1\)
+\defitem We use the fact that \(R\) doesn't constrain the behaviour of \(J_2\):
+	\begin{align*}
+		\sigma_0 \uplus \sigma_{01} \vdash R\mpar{s_0, s_{01}} \iff & \mpar{\bigwedge_{v_1 \in V_1} v_{1'} = v_1}\psubst{\sigma_{01'} \uplus \sigma_{02} \uplus \sigma_{01}} \\
+		\iff & \bigwedge_\subbox{v_1 \in V_1} \sigma_{01'}\mpar{v_{1'}} = \sigma_{01}\mpar{v_1} \\
+		\iff & \top
+	\end{align*}
+\defitem Let \(s \defobject \mpar{s_{1'}, s_2} \in S\) and \(s_1 \in S_1\).
 	We want to prove both
@@
 \item[\goal{0'}:] \(t\) is a transition built from \(t_1\) so it has its holes.
-	Additionnally either \(k \notin J'_1\) so \(J' = J'_1\) or \(k \in J'_1\) so \(J' = \emptyset \uplus J'_1 \setminus \mbrc{k}\) because \(A_2\) has no holes.
+	Additionnally either \(k \notin J'_1\) so \(J' = J'_1\) or \(k \in J'_1\) so \(J' = \emptyset \cup J'_1 \setminus \mbrc{k}\) because \(A_2\) has no holes.
 	Either case \(J'_1 \cap J = J'_1 \setminus \mbrc{k} = \mpar{J'_1 \setminus \mbrc{k}} \cap J_1 = J' \cap J_1\).
@@
 		\iff & \sigma \uplus \nu \vdash \mpar{\reach{A}\mpar{s} \wedge \bigwedge_{v_1 \in V_1} v_{1'} = v_1}\psubst{\psi \uplus \psi_1} \\
-		\iff & \sigma \uplus \nu \vdash \reach{A}\mpar{s}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1} \psi_{1'}\mpar{v_{1'}} = \psi_1\mpar{v_1} \\
-		\iff & \sigma \uplus \nu \vdash \reach{A}\mpar{s}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1 \uplus \fvars{t_1}} v_{1'} = v_1 \\
+		\iff & \sigma \uplus \nu \vdash \reach{A}\mpar{s}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1} \psi_{1'}\mpar{v_{1'}} = \psi\mpar{v_1} \\
+		\iff & \sigma \uplus \nu \vdash \reach{A}\mpar{s}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1 \cup \fvars{t_1}} v_{1'} = v_1 \\
 		\iff & \mpar{\sigma \vdash \reach{A}\mpar{s}\psubst{\psi}} \wedge \mpar{\sigma \uplus \nu \vdash \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1}
 	\end{align*}
-\item[\goal{1}:] Let \nmm{\sigma: V \uplus V_1 \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
-	We use dummy values for the variables in \nmm{\biguplus_\subbox{t \in \fOT{s}} \fvars{t}} to get the left side of the implication (independant from these values), immediately broken into
-	\begin{gather}
-		\sigma \vdash \reach{A}\mpar{s} \hyp{2a} \\
-		\sigma \vdash \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1 \hyp{2b} \\
-		\sigma \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{2c}
-	\end{gather}
-	\(\reach{A}\) is a witness of the non-locking composition so we have the hypothesis:
-	\[ V \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{3} \]
-	We use \hyp{3} with valuation \(\sigma\) to get \nmm{\nu: \biguplus_\subbox{t \in \fOT{s}} \fvars{t} \to \values}.
-	The left side of the implication is proved with \hyp{2a} and \hyp{2c}, the right side gives the hypothesis:
-	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{3'} \]
-	We prove \goal{1} with valuation \(\nu\) by admitting the left side of the implication and using \hyp{3'}.
+\item[\goal{1}:] % TODO: adapt and continue
+	Let \nmm{\sigma: V \uplus V_1 \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
+	We rename some variables in the input domain of \(\sigma\) to get \(\nu: \fvars{t_1} \to \values\).
 \end{proof}
 
-\subsection{Special composition correctness for hole-superset simulation}\label{apx:schs}
-Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and  \(A_3 \defobject \OAg[3]\) be open automata.
-Let \(k \in J_1 \setminus J_2\) and \(A \defobject A_1\subst{A_3}{k}\), with \(A = \OAg\).
-Let \(R_{12}\) be a hole-superset simulation of \(A_1\) by \(A_2\) and \(\reach{A}\) be a witness that \(A\) is non-locking.
-\[ R \defobject \mpar{\mpar{s_1, s_3}, s_2} \mapsto R_{12}\mpar{s_1, s_2} \wedge \reach{A}\mpar{s_1, s_3} \]
-We want to prove that \(R\) is a hole-superset simulation of \(A\) by \(A_2\).
+\subsection{Special composition correctness for hole-superset simulation}
 \begin{proof}
-\item[1)] \(J = J_3 \uplus J_1 \setminus \mbrc{k} \supseteq J_3 \uplus J_2 \setminus \mbrc{k} \supseteq J_2 \setminus \mbrc{k} = J_2\)
-\item[2)] We use the fact that \(R_{12}\) relates initial configurations and that initial configuration is reachable:
-	\begin{align*}
-		\sigma_0 \uplus \sigma_{02} \vdash R\mpar{s_0, s_{02}} \iff & \sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03} \vdash R_{12}\mpar{s_{01}, s_{02}} \wedge \reach{A}\mpar{s_0} \\
-		\iff & \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar{\sigma_0 \vdash \reach{A}\mpar{s_0}}
-	\end{align*}
-\item[3)] Let \(s \defobject \mpar{s_1, s_3} \in S\) and \(s_2 \in S_2\).
-	We want to prove both
-	\begin{align*}
-		& \bigsymb{\forall} t \defobject \OTg \in \fOT{s}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
-		& \quad \mpar{\forall x \in X, J'_{2x} \cap J = J' \cap J_2} \\[-10pt]
-		& \nwedge V \uplus V_2 \uplus \fvars{t} \vdash R\mpar{s, s_2} \wedge g \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J} \beta_j = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R\mpar{s', s'_{2x}}\psubst{\psi \uplus \psi_{2x}}
-		\end{array}} \goal{0}
-	\end{align*}
-	\[ V \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \goal{1} \]
-	Let \nmm{t \defobject \OTg \in \fOT{s}}, we use the fact that \(R_{12}\) is a simulation from the states \(\mpar{s_1, s_2}\) to get the hypothesis:
-	\begin{align*}
-		& \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
-		& \quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
-		& \nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R_{12}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}} \hyp{1}
-	\end{align*}
-	Transition \(t\) is obtained by composition of \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}} and \nmm{t_3 \defobject \OTx{3}{}{3}{3} \in \fOT{s_3}} if \(k \in J'_1\) or by a the first transition and the state \(s_3\) if \(k \notin J'_1\).
-	We use \hyp{1} with the transition \(t_1\) to get
-	\begin{gather*}
-		\mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X} \\
-		\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2 \hyp{1'} \\
-		V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R_{12}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}} \hyp{1"}
-	\end{gather*}
-	We will prove \goal{0} for the family \(t_{2x}\), the new goals are
-	\begin{gather}
-		\forall x \in X, J'_{2x} \cap J = J' \cap J_2 \goal{0'} \\
-		V \uplus V_2 \uplus \fvars{t} \vdash R\mpar{s, s_2} \wedge g \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J} \beta_j = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R\mpar{s', s'_{2x}}\psubst{\psi \uplus \psi_{2x}}
-		\end{array}} \goal{2}
-	\end{gather}
-\item[\goal{0'}:] Let \(x \in X\)
-	\begin{align*}
-		J'_{2x} \cap J & = J'_{2x} \cap \mpar{J_3 \uplus J_1 \setminus \mbrc{k}} \\
-		& = J'_{2x} \cap J_1 & \text{by } k \in J_1 \setminus J_2 \text{ and } \emptyset = J_3 \cap J_1 \supseteq J_3 \cap J_2 \hyp{2} \\
-		& = J'_1 \cap J_2 & \text{by \hyp{1'}} \\
-		& = \mpar{J'_1 \uplus J'_3} \cap J_2 \\
-		& = J' \cap J_2
-	\end{align*}
-\item[\goal{2}:] Let \nmm{\sigma: V \uplus V_2 \uplus \fvars{t} \to \values}.
-	We use dummy values for the variables in \nmm{\biguplus_\subbox{t_{2x} \in \fOT{s_2}} \fvars{t_{2x}}} to get the left side of the implication (independant from these values), immediately broken into
-	\begin{gather}
-		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{3a} \\
-		\sigma \vdash \reach{A}\mpar{s} \hyp{3b} \\
-		\sigma \vdash g \hyp{3c}
-	\end{gather}
-	We use \hyp{1"} with valuation \(\sigma\) on variables \(V_1 \uplus V_2 \uplus \fvars{t_1}\), which is possible because the composition of transitions doesn't remove any variable.
-	Then we get the values of the implicit \(\exists\) in \nmm{\nu: \biguplus_{x \in X} \fvars{t_{2x}}}.
-	The left side of the implication is proved with \hyp{3a} and \hyp{3c}.
-	So we get a \(x \in X\) such that
-	\begin{gather}
-		\sigma \uplus \nu \vdash \alpha_1 = \alpha_{2x} \hyp{4a} \\
-		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \hyp{4b} \\
-		\sigma \uplus \nu \vdash g_{2x} \hyp{4c} \\
-		\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \hyp{4d}
-	\end{gather}
-	In order to progress on \goal{2} we give valuation \(\nu\) for the implicit \(\exists\), admit the left side of the implication and choose to prove the branch \(x\):
-	\begin{gather}
-		\sigma \uplus \nu \vdash \alpha = \alpha_{2x} \goal{2a} \\
-		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_{2x} \cap J} \beta_j = \beta_{2xj} \goal{2b} \\
-		\sigma \uplus \nu \vdash g_{2x} \goal{2c} \\
-		\sigma \uplus \nu \vdash R\mpar{s', s'_{2x}}\psubst{\psi \uplus \psi_{2x}} \goal{2d}
-	\end{gather}
-	\goal{2a} is proved by \hyp{4a} (\(\alpha = \alpha_1\)).
-	\goal{2b} is proved using \hyp{4b} because \(J'_{2x} \cap J = J'_{2x} \cap J_1 = J'_1 \cap J_2\) (\hyp{2} and \hyp{1'}) and \(\forall j \in J'_1, \beta_{1j} = \beta_j\) (transition comes from composition).
-	\goal{2c} is proved by \hyp{4c}.
-	For \goal{2d} we use \hyp{4d} and \hyp{3b} with the preservation of reachability across transitions:
-	\begin{align*}
-		& \sigma \uplus \nu \vdash R\mpar{s', s'_{2x}}\psubst{\psi \uplus \psi_{2x}} \\
-		\iff & \sigma \uplus \nu \vdash \mpar{R_{12}\mpar{s'_1, s'_{2x}} \wedge \reach{A}\mpar{s}}\psubst{\psi_1 \uplus \psi_{2x} \uplus \psi_3} \\
-		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \reach{A}\mpar{s}\psubst{\psi}}
-	\end{align*}
-\item[\goal{1}:] 
-	Let \nmm{\sigma: V \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values}.
-	We use dummy values for the variables in \nmm{\biguplus_\subbox{t \in \fOT{s}} \fvars{t}} to get the left side of the implication (independant from these values), immediately broken into
-	\begin{gather}
-		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{5a} \\
-		\sigma \vdash \reach{A}\mpar{s} \hyp{5b} \\
-		\sigma \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{5c}
-	\end{gather}
-	\(R_{12}\) is a simulation and \(\reach{A}\) is a witness of the non-locking composition so we have the hypotheses:
-	\begin{gather}
-		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6} \\
-		V \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{7}
-	\end{gather}
-	We use \hyp{6} with valuation \(\sigma\) to get \nmm{\nu: \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
-	The left side of the implication is proved with \hyp{5a} and \hyp{5c}, the right side gives the hypothesis:
-	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{6'} \]
-	We then use \hyp{7} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t \in \fOT{s}} \fvars{t}}.
-	The left side of the implication is proved using \hyp{5b} and \hyp{6'}, the right side gives:
-	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{7'} \]
-	We prove \goal{1} with valuation \(\nu'\) by admitting the left side of the implication and using \hyp{7'}.
+% TODO
 \end{proof}
@@
 Let \(R_{12}\) be a hole-\(\triangle\) simulation of \(A_1\) by \(A_2\) and \(R_{23}\) of \(A_2\) by \(A_3\).
-\[ R \defobject \mpar{s_1, s_3} \mapsto \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \]
-We want to prove that \(R\) is a hole-\(\triangle\) simulation of \(A_1\) by \(A_3\).
+\[ R_{13} \defobject \mpar{s_1, s_3} \mapsto \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \]
+\(R_{13}\) is a hole-\(\triangle\) simulation of \(A_1\) by \(A_3\).
 \begin{proof}
-\item[1)] By transitivity of \(\triangle\), \(J_1 \triangle J_3\)
-\item[2)] We prove that initial configurations are related using \(\sigma_{02}\) as the values of the variables in \(V_2\), and \(s_{02}\) to choose the branch of the disjunction.
-\begin{align*}
-	\sigma_{01} \uplus \sigma_{03} \vdash R\mpar{s_{01}, s_{03}} \iff & \sigma_{01} \uplus \sigma_{03} \vdash \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_{01}, s_2} \wedge R_{23}\mpar{s_2, s_{03}} \\
+\defitem By transitivity of \(\triangle\), \(J_1 \triangle J_3\)
+\defitem We prove that initial configurations are related using \(\sigma_{02}\) as the values of the variables in \(V_2\), and \(s_{02}\) to choose the branch of the disjunction.
+\begin{align*}
+	\sigma_{01} \uplus \sigma_{03} \vdash R_{13}\mpar{s_{01}, s_{03}} \iff & \sigma_{01} \uplus \sigma_{03} \vdash \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_{01}, s_2} \wedge R_{23}\mpar{s_2, s_{03}} \\
 	\impliedby & \sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03} \vdash R_{12}\mpar{s_{01}, s_{02}} \wedge R_{23}\mpar{s_{02}, s_{03}} \\
@@
 \end{align*}
-\item[3)] Let \(\mpar{s_1, s_3} \in S_1 \times S_3\), we want to prove both
+\defitem Let \(\mpar{s_1, s_3} \in S_1 \times S_3\), we want to prove both
 	\begin{align*}
@@
 		& \mpar{\forall x \in X, J'_{3x} \cap J_1 = J'_1 \cap J_3} \\[-10pt]
-		& \wedge V_1 \uplus V_3 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_3} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+		& \wedge V_1 \uplus V_3 \uplus \fvars{t_1} \vdash R_{13}\mpar{s_1, s_3} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
 			\alpha_1 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x} \cap J_1} \beta_{1j} = \beta_{3xj} \\[12pt]
-			\nwedge g_{3x} \wedge R\mpar{s'_1, s'_{3x}}\psubst{\psi_1 \uplus \psi_{3x}}
+			\nwedge g_{3x} \wedge R_{13}\mpar{s'_1, s'_{3x}}\psubst{\psi_1 \uplus \psi_{3x}}
 		\end{array}} \goal{0}
 	\end{align*}
-	\[ V_1 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash R\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{1} \]
+	\[ V_1 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash R_{13}\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{1} \]
 \item[\goal{0}:] Let \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}}.
@@
 		\forall z \in Z, J'_{3z} \cap J_1 = J'_1 \cap J_3 \goal{0'} \\
-		V_1 \uplus V_3 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_3} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{z \in Z} \mpar{\everymath{\displaystyle}\begin{array}{l}
+		V_1 \uplus V_3 \uplus \fvars{t_1} \vdash R_{13}\mpar{s_1, s_3} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{z \in Z} \mpar{\everymath{\displaystyle}\begin{array}{l}
 			\alpha_1 = \alpha_{3z} \wedge \bigwedge_\subbox{j \in J'_{3z} \cap J_1} \beta_{1j} = \beta_{3zj} \\[12pt]
-			\nwedge g_{3z} \wedge R\mpar{s'_1, s'_{3z}}\psubst{\psi_1 \uplus \psi_{3z}}
+			\nwedge g_{3z} \wedge R_{13}\mpar{s'_1, s'_{3z}}\psubst{\psi_1 \uplus \psi_{3z}}
 		\end{array}} \goal{2}
@@
 	We use dummy values for variables in \nmm{\biguplus_\subbox{z \in Z} \fvars{t_{3z}}} to get the left side of this implication as an hypothesis (independant from these values):
-	\[ \sigma_1 \uplus \sigma_3 \vdash R\mpar{s_1, s_3} \wedge g_1 \hyp{4} \]
+	\[ \sigma_1 \uplus \sigma_3 \vdash R_{13}\mpar{s_1, s_3} \wedge g_1 \hyp{4} \]
 	Hypothesis immediately broken down into
@@
 	\end{align}
-	In order to progress on \goal{2} we give valuation \(\nu_3\) for the implicit \(\exists\), admit the left side of the implication and choose to prove the branch \(z\):
+	Finally to prove \goal{2} with valuation \(\nu_3\) for the implicit \(\exists\), we admit the left side of the implication choose to prove the branch \(z\):
 	\begin{align}
@@
 		\sigma_3 \uplus \nu_3 & \vdash g_{3z} \goal{2c} \\
-		\sigma_1 \uplus \sigma_3 \uplus \nu_3 &\vdash R\mpar{s'_1, s'_{3z}}\psubst{\psi_1 \uplus \psi_{3z}} \goal{2d}
+		\sigma_1 \uplus \sigma_3 \uplus \nu_3 &\vdash R_{13}\mpar{s'_1, s'_{3z}}\psubst{\psi_1 \uplus \psi_{3z}} \goal{2d}
 	\end{align}
@@
 	\begin{align*}
-		& \sigma_1 \uplus \sigma_3 \uplus \nu_3 \vdash R\mpar{s'_1, s'_{3z}}\psubst{\psi_1 \uplus \psi_{3z}} \\
+		& \sigma_1 \uplus \sigma_3 \uplus \nu_3 \vdash R_{13}\mpar{s'_1, s'_{3z}}\psubst{\psi_1 \uplus \psi_{3z}} \\
 		\iff & \mpar{R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}}\psubst{\psi_1 \uplus \psi_{3z}}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_1 \uplus \sigma_3 \uplus \nu_3} \\
@@
 		\forall s_2 \in S_2, V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash R_{23}\mpar{s_2, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{8} \\
-		\sigma_1 \uplus \sigma_3 \vdash R\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{1'}
+		\sigma_1 \uplus \sigma_3 \vdash R_{13}\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{1'}
 	\end{gather}
 	We use dummy values for variables in \nmm{\biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1}} to get the left side of this implication as an hypothesis (independant from these values):
-	\[ \sigma_1 \uplus \sigma_3 \vdash R\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \hyp{9} \]
+	\[ \sigma_1 \uplus \sigma_3 \vdash R_{13}\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \hyp{9} \]
 	Hypothesis that we immediately break down into:
@@
 	\end{gather*}
-	We can use \hyp{8} with state \(s_2\) and valuation \(\sigma_2 \uplus \sigma_3\) to get \nmm{\nu_2: \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values}.
+	We can use immediately \hyp{8} with state \(s_2\) and valuation \(\sigma_2 \uplus \sigma_3\) to get \nmm{\nu_2: \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values}.
 	The left side of the implication is proved with the right side of \hyp{9'} and \hyp{9"}, so we get
@@
 
-\section{Proof or properties for open automata refinement}
-
-\subsection{Context refinement}\label{apx:cr} % TODO HERE: adapt
-Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) be three open automata.
-Let \(k \in J_1\), \(A_{13} \defobject A_1\subst{A_3}{k}\) and \(A_{23} \defobject A_2\subst{A_3}{k}\).
-Let \(R_{12}\) be a hole-equal simulation of \(A_1\) by \(A_2\) and \(\reach{A_{13}}\) be a witness that \(A_{13}\) is non-locking.
-We pose \(A_{13} = \OAg[13]\) and \(A_{23} = \OAg[23]\).
-\[ R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \]
-Where \(y_{3x}\) is the renaming of \(y_3\) from \(A_3\) in \(A_{x3}\).
-We want to prove that \(R\) is a hole-equal simulation of \(A_{12}\) by \(A_{23}\).
-\begin{proof}
-\item[1)] \(J_{13} = J_3 \uplus J_1 \setminus \mbrc{k} = J_3 \uplus J_2 \setminus \mbrc{k} = J_{23}\) by \(J_1 = J_2\).
-\item[2)] For \(\sigma_{013} \uplus \sigma_{023} \vdash R\mpar{s_{013}, s_{023}}\) we use the fact that \(R_{12}\) relates inital configurations and initial configuration is reachable:
-	\begin{align*}
-		& \sigma_{013} \uplus \sigma_{023} \vdash R\mpar{s_{013}, s_{023}} \\
-		\iff & R\mpar{\mpar{s_{01}, s_{031}}, \mpar{s_{02}, s_{031}}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{031} \uplus \sigma_{032}} \\
-		\iff & R_{12}\mpar{s_{01}, s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}\psubst{\sigma_{013}} \wedge \mpar{\bigwedge_{v_3 \in V_3} v_{31} = v_{32}}\psubst{\sigma_{031} \uplus \sigma_{032}} \\
-		\iff & \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}} \wedge \bigwedge_\subbox{v_3 \in V_3} \sigma_{031}\mpar{v_{31}} = \sigma_{032}\mpar{v_{32}} \\
-		\iff & \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}} \wedge \top
-	\end{align*}
-\item[3)] Let \(s_{13} \defobject \mpar{s_1, s_{31}} \in S_{13}\) and \(s_{23} \defobject \mpar{s_2, s_{32}} \in S_{23}\).
-	We want to prove both
-	\begin{align*}
-		& \bigsymb{\forall} t_{13} \defobject \OTx{13}{}{13}{13} \in \fOT{s_{13}}, \bigsymb{\exists} \mpar{t_{23x} \defobject \OTx{23}{x}{23x}{23x} \in \fOT{s_{23}}}^{x \in X}, \\
-		& \quad \mpar{\forall x \in X, J'_{23x} \cap J_{13} = J'_{13} \cap J_{23}} \\[-10pt]
-		& \nwedge V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \Rightarrow \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\!\!\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \\[12pt]
-			\nwedge g_{23x} \wedge R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
-		\end{array}\!\!} \goal{0}
-	\end{align*}
-	\[ V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash R\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \goal{1} \]
-	Let \nmm{t_{13} \defobject \OTx{13}{}{13}{13} \in \fOT{s_{13}}}, we use the fact that \(R_{12}\) is a simulation from the states \(\mpar{s_1, s_2}\) to get the hypothesis:
-	\begin{align*}
-		& \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
-		& \quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
-		& \nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}} \hyp{1}
-	\end{align*}
-	Transition \(t_{13}\) is obtained in \(A_{13}\) by composition of two transitions \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}} and \nmm{t_{31} \defobject \OTx{31}{}{31}{31} \in \fOT{s_{31}}} if \(k \in J'_1\) or by a the first transition and the state \(s_{31}\) if \(k \notin J'_1\).
-	We use \hyp{1} with the transition \(t_1\) to get
-	\begin{gather*}
-		\mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X} \\
-		\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2 \hyp{1'} \\
-		V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}} \hyp{1"}
-	\end{gather*}
-	To build the family of transitions we need to know if \(k \in J'_{2x}\) for a every \(x \in X\):
-	\begin{align*}
-		J'_1 & = J'_1 \cap J_1 \\
-		& = J'_1 \cap J_2 & \text{by } J_1 = J_2 \\
-		& = J'_{2x} \cap J_1 & \text{by \hyp{1'}} \\
-		& = J'_{2x} \cap J_2 & \text{by } J_1 = J_2 \\
-		& = J'_{2x} \hyp{2}
-	\end{align*}
-	In the case \(s_{31} \neq s_{32}\) we can give the empty family, it won't cause any issue.
-	Otherwise \(s_{31} = s_{32}\) so we can copy \(t_{31}\) into \nmm{t_{32} = \OTx{32}{}{32}{32}} to avoid conflicts.
-	We also name \(t_3\) the original transition from \(T_3\).
-	Using \hyp{2} we can build the familly of transition generated by the family \(t_{2x}^{x \in X}\):
-	\[ t_{23x}^{x \in X} \defobject x \mapsto \choice{
-		\OT{\mpar{s_2, s_{32}}}{\mpar{s'_{2x}, s'_{32}}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x} \setminus \mbrc{k}} \uplus \beta_{3j}^{j \in J'_{32}}}{g_{2x} \wedge g_{32} \wedge \alpha_{32} = \beta_{2xk}}{\psi_{2x} \uplus \psi_{32}} & \text{if } k \in J'_{2x} \\
-		\OT{\mpar{s_2, s_{32}}}{\mpar{s'_{2x}, s_{32}}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_2}}{g_2}{\psi_2} & \text{otherwise}
-	} \]
-	We will prove \goal{0} for the family \(t_{23x}^{x \in X}\), the new goals are
-	\begin{gather}
-		\forall x \in X, J'_{23x} \cap J_{13} = J'_{13} \cap J_{23} \goal{0'} \\
-		V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \\[12pt]
-			\nwedge g_{23x} \wedge R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
-		\end{array}} \goal{2}
-	\end{gather}
-\item[\goal{0'}:] Let \(x \in X\), by case on \(k \in J'_1\):
-	\begin{align*}
-		\text{If } k \in J'_1: && J'_{23x} \cap J_{13} & = \mpar{J'_{31} \uplus J'_{2x} \setminus \mbrc{k}} \cap \mpar{J_3 \uplus J_1 \setminus \mbrc{k}} \\
-		&&& = \mpar{J'_{31} \cap J_3} \uplus \mpar{J'_{2x} \cap J_1} \setminus \mbrc{k} \\
-		&&& = \mpar{J'_{31} \cap J_3} \uplus \mpar{J'_1 \cap J_2} \setminus \mbrc{k} & \text{by \hyp{1'}} \\
-		&&& = \mpar{J'_{31} \uplus J'_1 \setminus \mbrc{k}} \cap \mpar{J_3 \uplus J_2 \setminus \mbrc{k}} \\
-		&&& = J'_{13} \cap J_{23} \\
-		\text{If } k \notin J'_1: && J'_{23x} \cap J_{13} & = \mpar{J'_{2x} \setminus \mbrc{k}} \cap \mpar{J_1 \setminus \mbrc{k}} \\
-		&&& = J'_{2x} \cap J_1 & \text{by } k \notin J'_1 = J'_{2x} \text{ \hyp{2}} \\
-		&&& = J'_1 \cap J_2 & \text{by \hyp{1'}} \\
-		&&& = \mpar{J'_1 \setminus \mbrc{k}} \cap \mpar{J_2 \setminus \mbrc{k}} & \text{by } k \notin J'_1 \\
-		&&& = J'_{13} \cap J_{23}
-	\end{align*}
-\item[\goal{2}:] Let \(\sigma: V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \to \values\).
-	We use dummy values for the variables in \nmm{\biguplus_{x \in X} \fvars{t_{23x}}} to get the left side of the implication as an hypothesis (independant from these values):
-	\[ \sigma \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \hyp{3} \]
-	If \(s_{31} \neq s_{32}\) then this hypothesis is \(\sigma \vdash \bot\), the empty family works and the proof is finished.
-	We can assume \(s_{31} = s_{32}\) and break \hyp{3} into
-	\begin{gather}
-		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{3a} \\
-		\sigma \vdash \reach{A_{13}}\mpar{s_{13}} \hyp{3b} \\
-		\sigma \vdash \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} \hyp{3c} \\
-		\sigma \vdash g_{13} \hyp{3d}
-	\end{gather}
-	We use \hyp{1"} with valuation \(\sigma\) on variables \(V_1 \uplus V_2 \uplus \fvars{t_1}\), which is possible because the composition of transitions doesn't remove any variable (the simplification steps do, they give bisimilar automata).
-	Then we get the values of the implicit \(\exists\) in \nmm{\nu: \biguplus_{x \in X} \fvars{t_{2x}}}.
-	The left side of the implication is proved with \hyp{3a} and \hyp{3d}.
-	So we get a \(x \in X\) such that
-	\begin{gather}
-		\sigma \uplus \nu \vdash \alpha_1 = \alpha_{2x} \hyp{4a} \\
-		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \hyp{4b} \\
-		\sigma \uplus \nu \vdash g_{2x} \hyp{4c} \\
-		\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \hyp{4d}
-	\end{gather}
-	If \(k \in J'_1\), we extend the valuation \(\nu\) to cover the variables of \(t_3\) in \(t_{23x}\) using their value in \(t_{13}\), \(\nu' \defobject \nu \uplus \mset{v_{32} \mapsto \sigma\mpar{v_{31}}}{v_3 \in \fvars{t_3}}\)
-	Otherwise \(\nu' \defobject \nu\).
-	We progress on \goal{2} by giving the valuation \(\sigma \uplus \nu'\) to the implicit \(\exists\), admitting the left side of the implication and choosing to prove the branch \(x\) of the disjunction:
-	\begin{gather}
-		\sigma \uplus \nu' \vdash \alpha_{13} = \alpha_{23x} \goal{3a} \\
-		\sigma \uplus \nu' \vdash \bigwedge_\subbox{j \in J'_{23x} \cap J_{13}} \beta_{13j} = \beta_{23xj} \goal{3b} \\
-		\sigma \uplus \nu' \vdash g_{23x} \goal{3c} \\
-		\sigma \uplus \nu' \vdash R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}} \goal{3d}
-	\end{gather}
-	Because composition doesn't change the produced actions nor its variables, \goal{3a} is proved by \hyp{4a}.
-	\goal{3b} holds because the valuations for the actions of the holes in \(J_3\) coincide by definition of \(\nu'\) and by \hyp{4b} for the others.
-	For \goal{3c} we have two cases, if \(k \notin J'_1\) then \(g_{23x} \equiv g_{2x}\) and \hyp{4c} is sufficient, if \(k \in J'_1\) then \(g_{23x} \equiv g_{2x} \wedge g_3 \wedge \alpha_3 = \beta_{2xk}\) so we also need \hyp{3d} (\(g_{13} \equiv g_1 \wedge g_3 \wedge \alpha_3 = \beta_{1k}\)) and \hyp{4b} for the value \(k\) (\(\beta_{1k} = \beta_{2xk}\)).
-	\goal{3d} is proved using \hyp{4d}, \hyp{3b} with the preservation of reachability across transitions (+ \hyp{3d}), \hyp{3c} and the fact that \(A_3\) performs the same transition with same values in both composed automata:
-	\begin{align*}
-		& \sigma \uplus \nu' \vdash R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}} \\
-		\iff & \sigma \uplus \nu' \vdash \mpar{R_{12}\mpar{s'_1, s'_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32}}\psubst{\psi_1 \uplus \psi_{31} \uplus \psi_{2x} \uplus \psi_{32}} \\
-		\iff & \sigma \uplus \nu' \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}} \wedge \bigwedge_\subbox{v_3 \in V_3} \psi_{31}\mpar{v_{31}} = \psi_{32}\mpar{v_{32}} \\
-		\iff & \sigma \uplus \nu' \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}} \wedge \bigwedge_\subbox{v_3 \in V_3 \uplus \fvars{t_3}} v_{31} = v_{32} \\
-		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}}} \wedge \mpar{\sigma \vdash \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32}}
-	\end{align*}
-\item[\goal{1}:] Let \nmm{\sigma: V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \to \values}.
-	We use dummy values for the variables in \nmm{\biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}}} to get the left side of the implication (independant from these values), immediately broken into
-	\begin{gather}
-		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{5a} \\
-		\sigma \vdash \reach{A_{13}}\mpar{s_{13}} \hyp{5b} \\
-		\sigma \vdash \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \hyp{5c}
-	\end{gather}
-	\(R_{12}\) is a simulation and \(\reach{A_{13}}\) is a witness of the non-locking composition so we have the hypotheses:
-	\begin{gather}
-		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6} \\
-		V_{13} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{7}
-	\end{gather}
-	We use \hyp{6} with valuation \(\sigma\) projected on the variables from generating transitions in \(A_2\) to get \nmm{\nu: \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
-	The left side of the implication is proved using \hyp{5a} and \hyp{5c} because the guards from transitions of \(A_2\) are still in transitions of \(A_{23}\), the right side gives:
-	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6'} \]
-	We then use \hyp{7} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}}}.
-	The left side of the implication is proved using \hyp{5b} and \hyp{6'}, the right side gives:
-	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{7'} \]
-	\goal{1} is proved for valuation \(\nu'\) by admitting the left side and using \hyp{7'}.
-\end{proof}
-
-\subsection{Congruence for composition}\label{apx:cong}
-
-\subsection{compatibility with FH-bisimulation}\label{apx:FHbcomp}
-
 \end{document}

### 2021-06-14 2021-Refinement/report.tex

--- 2021-06-13 2021-Refinement/report.tex
@@
 \section{Introduction}
-The open automata model is used to give the semantic of open pNets \cite{2007.10770}.
+The open automata model was originally designed to give the semantic of open pNets \cite{2007.10770}.
 Open pNets are not petri nets but an intermediate representation used in the VerCors project to perform verification \cite{henrio:01252323}.
  Verification is the process of checking that an implementation satisfies a specification.
-Open pNets with the open automaton semantics and equivalence relation introduced in previous work \cite{2007.10770} were sucessfully used to model and verify BIP and GCM \cite{qin:01823507, ameurboulifa:01526055}.
-However equivalences relations are not always sufficient to perform verification, refinement relations are also used.
-For instance an example of open pNet where equivalence is not sufficient was encountered in an article about algorithms fo weak bisimulation on open automata \cite{wang:03126313}.
-
-The contributions of this article are the definition of composition for open automata without having to define open pNets, and the introduciton of several refinement relations for open automata.
+\Ludo{verification is more general than that (or you need to refine specification): checking typing or absence of deadlocks belong to verification}
+Open pNets with the open automaton semantics and equivalence relation introduced in previous work \cite{2007.10770} were sucessfully used to model and verify some properties of applications based on BIP  and GCM \cite{qin:01823507, ameurboulifa:01526055} \Ludo{cite and expand acronym (x2)}.
+However equivalence relations are not always sufficient to perform verification, refinement relations are also used. \Ludo{verification/refinement/equivalence needs to be refined and explained}
+For instance a usecase where open pNet where equivalence is not sufficient can be found  in an article about algorithms fo weak bisimulation on open automata \cite{wang:03126313}.
+
+\Ludo{choose: either 1) you do not refer to open pnets below and explain informally open automata here (why are they useful, what makes them different from automata), or 2) you want to refer to pnets in the following and you explain informally pnets, uatomata and the relation}
+
+The contributions of this article are \Ludo{report?} the definition of composition for open automata without having to define open pNets, and the introduction of several refinement relations for open automata.
 % TODO: expand
@@
 % TODO: Related work: thesis
+
+\Ludo{RAPPEL: pour ecrire une intro: 1) on ecrit les contribs, 2) on explique avant les termeis techniques pour que le lecteur comprenne les contribs, 3) quand on a quasi fini le reste on ecrit le plan.
+ON peut commencer 1 et 2 un peu tot meme si il faut rediger le tout assez tard: on peut pas ecrire proprement un article sans avoir en tete les contribs de celui ci}
 
@@
 In Section \ref{sec:def} we give a clean and up to date definition of open automata.
-In Section \ref{sec:comp} we define their composition without requiring the use of open pNets.
-In Section \ref{sec:proofelts} we adapt the standard properties related to refinement relation from LTS to open automata.
-After that Section \ref{sec:prelref} is dedicated to progressively build a refinement relation.
+In Section \ref{sec:comp} we define their composition without requiring the use of open pNets \Ludo{does this mean that previous definitions were using open pnets?
+this might be clarified in contributions but when you redo a definition you must highlight why a new definition was necessary}.
+In Section \ref{sec:proofelts} we adapt several standard properties that we use in the definition of refinement relation from LTS to open automata.
+After that Section \ref{sec:prelref} is dedicated to progressively build a refinement relation and explain the elements of this construction.
 Section \ref{sec:refinement} introduces and analyses the refinement relation on open automata.
-Finally Section \ref{sec:ccl} recapitulates the contribution and present the work left.
+Finally Section \ref{sec:ccl} recapitulates the contribution and presents the work left.
 

### 2021-06-14 2021-Refinement/report.tex
reached page 4

@@
 Families of values, or equivalently maps will be noted \(\mset{i \mapsto x_i}{i \in I}\), \(\mset{i \gets x_i}{i \in I}\) or \(x_i^{i \in I}\).
-The latter can only be used if there is a generating expression; for instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\).
+The latter can only be used if there is a generating expression\Ludo{c est vrai pour les exemples mais pas pour les defs generiques (OA, bisim, ...): reformuler}; for instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\).
 However \(\mbrc{\alpha \mapsto 1, \beta \mapsto 2, \gamma \mapsto 3}\) has no generating expression and is represented here with the finite version of first notation.
@@
 There are several ways of ensuring a union is disjoint, we will indifferently either suppose sets are disjoint or rename conflicting object (useful for variables).
-The disjoint union of two maps \(\varphi: I \to X\) and \(\psi: J \to Y\) with \(I \cap J = \emptyset\) is \(\varphi \uplus \psi: I \uplus J \to X \cup Y\).
+The disjoint union of two maps \(\varphi: I \to X\) and \(\psi: J \to Y\) with \(I \cap J = \emptyset\) has the following signature \(\varphi \uplus \psi: I \uplus J \to X \cup Y\).
 
@@
 
-The terms \(\terms\) is a term algebra.
+Notations are parameterised by a term algebra \(\terms\).
 As any term algebra it has constant symbols with arity, variables, and a typing mechanism to distinguish well-formed and ill-formed terms.
 The action algebra \(\actions\) is another term algebra.
-It can be a subset of the terms.
+It can be \Ludo{''can be'' is not much informative} a subset of the terms.
 The formulas \(\formulas\) are at least the first order formulas over \(\terms\) and \(\actions\).
@@
 The formulas contain at least first order logic terms with an equality relation.
-This equality relation is not necessarily a syntactic equality (\(2 + 2 \neq 4\) with a syntactic equality).
-
-An example of term algebra can be Peano integers (constant zero with arity 0, constant successor function with arity 1 and the variables), the formulas associated can use syntactic equality relation, the sum relation \(\mathit{sum}\mpar{a, b, c}: \text{``}a = b + c\text{"}\) and the product relation \(\mathit{prod}\mpar{a, b, c}: \text{``}a = b \times c\text{"}\).
+This equality relation is not necessarily a syntactic equality (\(2 + 2 \neq 4\) with a syntactic equality but it is more expressive to consider that the two terms are equal).
+
+An example of term algebra can be Peano integers (constant zero with arity 0, constant successor function with arity 1 and the variables), the formulas associated can use syntactic equality relation, the sum relation \(\mathit{sum}\mpar{a, b, c}: \text{``}a = b + c\text{"}\), and the product relation \(\mathit{prod}\mpar{a, b, c}: \text{``}a = b \times c\text{"}\).
 
@@
 The interpretation of terms is supposed to be decidable.
-The satisfiability of formulas might not be decidable nor complete nor consistent, however we will pretend like they are because these are really hard problems for logicians that we don't want to deal with.
+The satisfiability of formulas might not be decidable nor complete nor consistent,
+but we will consider in the following that they are; this can be achieved by restricting the term algebra to a decidable subset.
 For instance a formula with quantifiers on variables might not be provable even if it is true for all values of these variables.
-In practise the formulas will be given to a SMT solver and we cannot always make sure they have all the previous properties.
+In practice the formulas will be given to a SMT solver and we cannot always make sure they have all the previous properties but, as soon as the satisfiability is consistent our theory is consistent too.
 \(\vdash\) can hence be interpreted as an indicator of what is given to the SMT; it separates the external logic and the logic on \(\formulas\).
@@
 This is correct when \(\values \subseteq \rterms\) and we suppose it is the case.
-Otherwise it doesn't invalidates theorems because it can stand as a shorthand for substitution with any term which is interpreted the kept value.
+Otherwise it doesn't invalidates theorems because it can stand as a shorthand for substitution with any term which is interpreted the kept value \Ludo{comprends pas la fin de phrase, anglais?}.
 We suppose that the interpretation of terms is compatible w.r.t.\@ substitution, that is if two terms \(t\), \(t'\) are interpreted with the same value, then replacing \(t\) by \(t'\) in a well-formed expression makes an equivalent well-formed expression.
@@
 The variable names may clash when considering two automata, in this case we suppose that we can still distinguish the variables in the formulas.
-In practise the open automata are used in a toolchain at a point where what came before guarantees there are no name clash, which is why we make this assumption.
-
-The initial valuation may be a partial valuation of the variables.
+In practice the open automata are used in a toolchain  that guarantees there are no name clash.
+
+The initial valuation is a partial valuation of the variables.
 If an undefined variable is set before being read, it behaves like an initially set variable.
 If an undefined variable is not set before being read then its value may be any fixed value.
-When refining the automaton it can be set by the implementation, or it can be left unspecified as a parameter of the automaton (for instance a \(n\) bits register has \(n\) as parameter).
+When refining \Ludo{bizarre de parler de rafinement ici: phrase a deplacer ou introduire par: Later we will consider refinement of autoamata and ....} the automaton it can be set by the implementation, or it can be left unspecified as a parameter of the automaton (for instance a \(n\) bits register has \(n\) as parameter).
 \begin{defi}[Open transition]
-An open transition is a tuple \nmm{\OTg} with \(s, s' \in S\) the source and target states, \(\alpha \in \actions\) the produced action, \(J' \subseteq J\) the holes involved in the transition, \(\beta_j \in \actions\) the actions of the holes, \(g \in \formulas\) the guard and \(\psi: V \to \terms\) the variables assignements.
+An open transition is a tuple \nmm{\OTg} with \(s, s' \in S\) the source and target states, \(\alpha \in \actions\) the produced action, \(J' \subseteq J\) the holes involved in the transition, \(\beta_j \in \actions\) the actions of the holes, \(g \in \formulas\) the guard and \(\psi: V \to \terms\) the variable assignments.
 \end{defi}
@@
 
-The intuition of an open automaton is a partially defined LTS with variables, guards on transitions and parametrised actions.
+The intuition of an open automaton is a partially defined LTS with variables, guards on transitions, and parametrised actions.
+The LTS is partial in the sense that one cn plug an LTS in the hole and the surrounding LTS will react to the actions emitted by the sub-LTS put in the hole.
 Initially the automaton is in the initial state with an extension on all the variables of the initial valuation.
 In any configuration, it can perform effective transitions which source state is the current state and which guard is satisfiable in the current valuation if the holes emit the indicated actions.
-An effective transition is a transition where every variable that is not an automaton variable is instanciated with a value.
-By performing the effective transition, the automaton emits the indicated action and updates its configuration according to the target state and variables assignements.
+An effective transition is a transition where every variable that is not an automaton variable is instantiated with a value.
+By performing the effective transition, the automaton emits the indicated action and updates its configuration according to the target state and variable assignments.
 
@@
 The FH-bisimulation \cite{henrio:01055091} is noted \(\cong\).
+
+\Ludo{here the reader needs either an intuition of the FH bisim or a definition in any case, he needs to know that he will get one or the other and when.
+For example we give below an intuitive definition of the FH bisim based on examples.}
+
+\Ludo{ If you need the notation but the def is not important you can explicitly say that the readers should refer to ??
+for the details of the def, but here I do not believe it is wise OR you could say FH bisim is useless and you do not introduce the notation but you should not use it afterwards (again not adapted I believe)}
 
@@
 The \(\act{accept}\) action is shortened as \(\act{acc}\) in the examples.
-During the synchronised action, the value returned by first agent is passed to the second agent.
+During the synchronised action, the value returned by the first agent is passed to the second agent.
 \begin{exi}[Enable, state-oriented]

### 2021-06-14 2021-Refinement/report.tex
finished reading sec 4

@@
 It would have avoided many effective transitions with trivially false guards like the one where \(x \mapsto 1, y \mapsto 2\), which has the guard \(1 = 2\).
+\Ludo{I believe that with the usual definition of the semantics of open automata it is the same ...
+please check: you do all potential transitions with the conditions that x is the same in both.
+In any case as the matching is not linear, the simplification is not obvious}
 
@@
 \end{defi}
-The goal of the extractor \(\fvars{t}\) when \(t\) is a transition is to get variables that are unique to that transition.
-Other variables like automaton variables are already known at this point so there is no use in getting them.
+
+The goal of the extractor \(\fvars{t}\) when \(t\) is a transition is to get variables that are unique \Ludo{what do you mean by unique here?} to that transition.
+Other variables like automaton variables are already known at this point so there is no use in getting them \Ludo{this is not clear because I do not know what variables you ``NEED'' to ``GET'' (need and get are strange and vague to me)}.
 Also the use of this extractor benefits from this exclusion: otherwise there would always be \(\setminus V\) following it to prevent variable shadowing.
+
+\Ludo{is it really variable shadowing?}
+
+\Ludo{you do not necessarily need to explain everything if this is what you need, but you miss an intuition of what this set is}
 
@@
 It is an alternative implementation of the enable operator which is FH-bisimilar to the previous one \cite{henrio:01299562}.
-Note that in this example \(r\) and \(l\) are a hole names and also closed terms: this is a naming conflict, though it is not ambiguous because \(J \cap \rterms = \emptyset\) always holds.
-The variables local to a transition are all the unbound variables in the expressions minus the automaton variables.
+\Ludo{makes no sense: FH bisimlar is still undefined, neither formally nor informally}
+Note that in this example \(r\) and \(l\) are a hole names and also closed terms: this is a naming conflict, though it is not ambiguous because \(J \cap \rterms = \emptyset\) always holds \Ludo{the intersection is at the same time empty and non-empty, why not use a different value (or underline them) or just say that they are in fact different names though it is easier to read using r and l for both}.
+\Ludo{le probleme ici c est qu on a l impression que tu essayes a la fois d etre tres strict et formel et pas vraiment en meme temps, il faut choisir}
+The variables that are said to be local to a transition are all the unbound variables in the expressions minus the automaton variables.
 For instance \(v\) is a variable of the automaton (used in the guard).
 It is not local to the transition.
-In a run, when taking effective transitions (without local variables), its value is not substituted with a closed term.
+\Ludo{je comprends ps cette phrase:} In a run, when taking effective transitions (without local variables), its value is not substituted with a closed term.
 For instance \nmm{\OT{»}{»}{\tau}{\mbrc{l \mapsto \tau}}{v = l \wedge \tau \neq \delta}{\mbrc{}}} is an effective transition generated from the second transition but not \nmm{\OT{»}{»}{\tau}{\mbrc{l \mapsto \tau}}{l = l \wedge \tau \neq \delta}{\mbrc{}}} (result of the forbidden substitution \(v \mapsto l\)).
 
-An imaginary run of this open automaton can be: The automaton in the hole \(l\) emits many actions, this synchronises with the only transition possible at that moment because \(v = l\).
+An  run of this open automaton can be: The automaton in the hole \(l\) emits many actions, this synchronises with the only transition possible at that moment because \(v = l\).
 Then the automaton in hole \(l\) emits a \(\delta\mpar{t}\), this is synchonised with the action that sets \(v \gets r\) and the automata in hole \(r\) must emit a \(\act{acc}\mpar{t}\).
@@
 
-Another imaginary run can be: The automaton in the hole \(l\) emits a sequence of non \(\delta\mpar{t}\) actions so the automaton in the hole \(r\) cannot emit a \(\act{acc}\mpar{t}\) and never runs.
+Another  run can be: The automaton in the hole \(l\) emits a sequence of non \(\delta\mpar{t}\) actions so the automaton in the hole \(r\) cannot emit a \(\act{acc}\mpar{t}\) and never runs.
 \end{exi}
 
-From this point open automata and open transitions can be called automata and transitions for simplicity. % NEED NORMALISATION, LEFT IN CASE OF OMISSION
+From this point open automata and open transitions are sometimes called automata and transitions for simplicity. % NEED NORMALISATION, LEFT IN CASE OF OMISSION
 
 \section{Composition of Open Automata}\label{sec:comp}
-Open automata are partially specified automata, part of that partiality comes from the holes.
-The interpretation of a hole is an interface with another open automaton, in which we can plug an open automaton with an operation called composition.
-In this article, composition will only refer to filling holes, other compositions like ``parallel composition" (pure interleaving) are not tackled.
-The composition of open automata was already implicitely defined by the means of composition on pNets in previous work \cite{henrio:01299562} but never completely formalised on open automata.
+Open automata are partially specified automata, that partiality comes mostly from the holes.
+The interpretation of a hole is an interface with another open automaton, in which we can plug an open automaton. The plugging operation is called composition.
+In this article, composition will only refer to filling holes, other compositions like ``parallel composition" (pure interleaving) are not tackled (but one can define an open automaton that performs the parallel composition of two others).
+The composition of open automata was already implicitly defined by the means of composition on pNets in previous work \cite{henrio:01299562} but never completely formalised on open automata.
 The definition of composition below is a direct translation of what happens with pNets composition without the need of introducing pNets.
 \begin{defi}[Composition of open automata]
-The composition of \(A_c \defobject \OAg[c]\) in the hole \(k \in J_p\) of \(A_p \defobject \OAg[p]\) is
+The composition of \(A_c \defobject \OAg[c]\) in the hole \(k \in J_p\) of \(A_p \defobject \OAg[p]\) is an open automaton defined as follows.
 \begin{align*}
@@
 The action emitted when \(A_c\) makes a transition is sychronised with the action of the hole \(k\) in transitions of \(A_p\) which have it as a hole action (first transition set, \(\alpha_c = \beta_k\)).
-The composition may look like a handshake, with both automata running in parallel (product of states and joint variables) however it is asymmetric because of the second transition set (\(k \notin J'_p\)):
-No transition of \(A_c\) is performed when a transition that do not refer to the hole \(k\) is performed in \(A_p\).
+The composition may look like a handshake, with both automata running in parallel (product of states and joint variables) however it is asymmetric because it is the first automaton that decides when the second can evolve, while the first automaton can evolve independently as soon as the hole is not involved in the open transition considered.
 
 Composition is a complex process that generates big automata with complex and potentially simplifiable transitions.
-However simplification is a hard problem that is not yet automatised on open automata, so from this point the guards and transitions will always be simplified by hand without further explaination.
+However simplification is a hard problem that is not yet automatised on open automata, so from this point the guards and transitions will always be simplified by hand without further explanation.
 An example of composition can be found in Appendix \ref{apx:composition}.
@@
 Even if an automaton is composed in two distinct holes it does not share its variables, each composition makes the cartesian product of states and a disjoint union of the variables.
-In practise, variables may have to be renamed.
+In practice, variables may have to be renamed.
 

### 2021-06-14 2021-Refinement/report.tex
more comments

@@
 \end{align*}
-It is an alternative implementation of the enable operator which is FH-bisimilar to the previous one \cite{henrio:01299562}.
-\Ludo{makes no sense: FH bisimlar is still undefined, neither formally nor informally}
-Note that in this example \(r\) and \(l\) are a hole names and also closed terms: this is a naming conflict, though it is not ambiguous because \(J \cap \rterms = \emptyset\) always holds \Ludo{the intersection is at the same time empty and non-empty, why not use a different value (or underline them) or just say that they are in fact different names though it is easier to read using r and l for both}.
+It is an alternative implementation of the enable operator which is \Ludo{FH-bisimilar}{makes no sense: FH bisimlar is still undefined, neither formally nor informally} to the previous one \cite{henrio:01299562}.
+Note that in this example \(r\) and \(l\) are a hole names and also closed terms: this is a naming conflict, though it is not ambiguous because \(J \cap \rterms = \emptyset\) always holds \Ludo{}{the intersection is at the same time empty and non-empty, why not use a different value (or underline them) or just say that they are in fact different names though it is easier to read using r and l for both}.
 \Ludo{le probleme ici c est qu on a l impression que tu essayes a la fois d etre tres strict et formel et pas vraiment en meme temps, il faut choisir}
@@
 It is not local to the transition.
-\Ludo{je comprends ps cette phrase:} In a run, when taking effective transitions (without local variables), its value is not substituted with a closed term.
+\Ludo{In a run,}{je comprends ps cette phrase:}  when taking effective transitions (without local variables), its value is not substituted with a closed term.
 For instance \nmm{\OT{»}{»}{\tau}{\mbrc{l \mapsto \tau}}{v = l \wedge \tau \neq \delta}{\mbrc{}}} is an effective transition generated from the second transition but not \nmm{\OT{»}{»}{\tau}{\mbrc{l \mapsto \tau}}{l = l \wedge \tau \neq \delta}{\mbrc{}}} (result of the forbidden substitution \(v \mapsto l\)).
@@
 The first is between states of two specific automata (\(R \subseteq S_1 \times S_2\)), the second is between automata (\(A_1 \leq A_2\)).
-Generally the second is implicit because its definition is always \(\exists R \subseteq S_1 \times S_2, P\mpar{R}\) with \(P\) a property, and only talking about \(R\) and \(P\) is sufficient.
+\Ludo
+{Generally the second is implicit because its definition is always \(\exists R \subseteq S_1 \times S_2, P\mpar{R}\) with \(P\) a property, and only talking about \(R\) and \(P\) is sufficient.}{je comprends pas cette phrase}
 However later on in this article we will define more complex relations on automata so we clarify the distinction now.
@@
 Reflexivity, transitivity and preorder are classical properties on relations.
-Correctness w.r.t.\@ composition means that every composition is considered a refinement.
-This property captures the expected behaviour of a refinement relation on a compositionnal structure like the open automata.
+Correctness w.r.t.\@ composition means that every composition is considered a refinement. \Ludo{problem}{ you have not yet said that your relation was a refinement!}
+This property captures the expected behaviour of a refinement relation on a compositional structure like the open automata.
 Completeness w.r.t.\@ composition means that a refinement corresponds to the left automaton being equivalent to some composition of the right automaton.
 This property is useful if we want to characterise the kind of operations that can generate any refined automaton starting from the specification.
+\Ludo{}{I do not understand this: what is the domain of the valuation?}
 We won't have it because extending the domain of the initial valuation will be a refinement which can't be expressed with composition.
@@
 Compatibility with composition is the conjunction of the two latter (assuming the relation is a preorder).
-This property is required on compositionnal structures to be of any use in verification, proofs and for model checking.
+This property is required on compositional structures to be of any use in verification, proofs and for model checking.
 Finally compatibility with FH-bisimulation is the refinement not being able to distinguish two FH-bisimilar automata.
@@
 
+\Ludo{ }{I do not understand the english + too many important properties you should give a hierarchy or at least find a better transition}
 The important properties we consider for the relation on states are being a simulation and the prevention of deadlocks as defined in the following definitions.
@@
 Here we assume that one of the related open automata can be obtained by composing an open automaton in a hole, open automaton which can have holes itself.
-This implies that there is no relation between their holes, for instance composing \(A_i\) in \(j_i\) (\(1 \leq i \leq n\)) of \(A_0\) gives the set of holes \(J \defobject \mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}\) that is neither subset nor superset of \(J_0\).
+This implies that there is no relation between \Ludo{their}{whose?
+refine} holes, for instance composing \(A_i\) in \(j_i\) (\(1 \leq i \leq n\)) of \(A_0\) gives the set of holes \(J \defobject \mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}\) that is neither subset nor superset of \(J_0\).
 Yet we still assume that in holes with the same name, the same open automaton will be composed.
@@
 However it is not sufficient to imply properties on the relation on automatons like being a preorder.
-It is only a necessary condition for any relation that will be defined with ``simulation" in its name.
+It is only a necessary condition that we put on any relation that we call a ``simulation'' in the following.
 
 Deadlocks are reachable configurations from which no further transition is possible.
-They can arise unpredictably when parallelism is involved (which is the case in our composition) and they break the intended behaviour of a system.
-By preventing them we could hope that the refinement preserves some liveness properties.
+They can arise unpredictably when parallelism is involved (which is the case in our composition) and they generally break the intended behaviour of a system.
+By preventing them we \Ludo{could}{This seems to say that it is useless to prevent them} hope that the refinement preserves some liveness properties.
 \begin{defi}[Deadlock prevention, intuitive definition]
@@
 \defitem It is a pre-simulation;
-\defitem If from related states, there is a possible transition in the specification, then there is a pair of matching transition:
+\defitem If from related states, there is a possible transition in the \Ludo{specification}{I do not believe specification has been defined nor implementation}, then there is \Ludo{a pair of matching transition}{A matching transition in the IMPLEMENTATION}:
 \begin{multline*}
@@
 \end{defi}
-Actually, this requirement prevents the presence of deadlock state in the first automaton if there is a related non-deadlock state in the second by contraposition.
-On top of that the transition preventing the deadlock has to be an existing transition in the specification.
-This is because a valid transition unmatched in the specification is not a deadlock, yet we do not want it.
-The direct formulation of the property would also have required the unintuitive quantification on a possibly empty set of transition to state that they are impossible.
+Actually, this requirement prevents the presence of deadlock state in the first automaton if there is a related non-deadlock state in the second by \Ludo{contraposition}{The contraposition is too tricky for me: are you sure?}.
+Additionally, the transition preventing \Ludo{the deadlock}{in the implementation?
+how can it be the same?why is there a single one?
+this sentence makes no sense to me} has to be an existing transition in the specification.
+This is because a valid transition unmatched in the specification \Ludo{is not a deadlock}{how can a transition be a deadlock? I am completely lost}, yet \Ludo{we do not want it}{too informal}.
+The \Ludo{direct formulation}{usually you say ``the direct'' when the property seems to be defined negatively which is syntactically not the case here: you should explain or remove the remark} of the property would also have required the unintuitive quantification on a possibly empty set of transition to state that they are impossible.
 The two previous reasons motivated the formulation in contraposed form.
@@
 In particular filling a hole with the deadlock automaton (only one state without out-transitions) is not considered a refinement for a deadlock reducing relation.
-A way to solve these conflicts is to characterise a composition that do not introduce deadlocks, which will be used instead of the composition introduced earlier.
+
+\Ludo{Here or before you should explain exactly WHAT YOU WANT: I do not know which are the required property which you will achieve which are incompatible, or state that you will now investigate each property and state whether it is desired / achievable/ compatible with the others: without this analysis the reader is lost}{}
+
+A way to solve \Ludo{these conflicts}{which conflict?
+can be clarified by answering the previous remark} is to characterise a composition that do not introduce deadlocks, which will be used instead of the composition introduced earlier.
 \begin{defi}[Reachability]

### 2021-06-15 2021-Refinement/report.tex
new intro paragraph for properties, might solve some of the issues

@@
 Because of composition, a relation as strong as simulation must be used.
+
+\Ludo{New}{je suggere un paragraphe du style}
+In this section we present a set of  properties that can be desirable for a refinement relation.
+We reach a point where we state a property that guarantees that the refinement does not create additional deadlock.
+Unfortunately, in the general case, this property is contradictory with the other ones, this is why we restrict the general composition defined before so that we only consider a composition  to be valid if it does not create deadlocks.
+With this new condition on validity of composition we are able to define in the next sections a refinement relation where most of the properties of interest are satisfied.
 

### 2021-06-15 2021-Refinement/Open_vending_machine.tex
Forgot to add some examples

\begin{tikzpicture}
\node[state,initial] (v0) at (0,0) {I};
\node[state] (v1) at (-6,0) {T};
\node[state] (v2) at (6,0) {C};
\draw (v0) ++(0,-1.5) edge[near start,init={m \gets 0}] (v0);
\draw (v0) edge[dir=90] node {\OTd{\act{money}\mpar{x}}{mon \mapsto \act{credit}\mpar{x}}{m \gets m + x}} (v0);
\draw (v0) edge[bend left,looseness=0] node {\OTd{\act{tea}\mpar{}}{}[m \geq 150]{m \gets m - 150}} (v1);
\draw (v1) edge[bend left,looseness=0] node {\OTd{\act{serve}\mpar{\mathit{tea}, x}}{serv \mapsto \act{tea}\mpar{x}}{}} (v0);
\draw (v0) edge[bend left,looseness=0] node {\OTd{\act{coffee}\mpar{}}{}[m \geq 150]{m \gets m - 150}} (v2);
\draw (v2) edge[bend left,looseness=0] node {\OTd{\act{serve}\mpar{\mathit{coffee}, x}}{serv \mapsto \act{coffee}\mpar{x}}{}} (v0);
\end{tikzpicture}

### 2021-06-15 2021-Refinement/Vending_machine.tex
Forgot to add some examples

--- 2021-06-15 2021-Refinement/Open_vending_machine.tex
@@
 \draw (v0) ++(0,-1.5) edge[near start,init={m \gets 0}] (v0);
-\draw (v0) edge[dir=90] node {\OTd{\act{money}\mpar{x}}{mon \mapsto \act{credit}\mpar{x}}{m \gets m + x}} (v0);
+\draw (v0) edge[dir=90] node {\OTd{\act{money}\mpar{x}}{}{m \gets m + x}} (v0);
 \draw (v0) edge[bend left,looseness=0] node {\OTd{\act{tea}\mpar{}}{}[m \geq 150]{m \gets m - 150}} (v1);
-\draw (v1) edge[bend left,looseness=0] node {\OTd{\act{serve}\mpar{\mathit{tea}, x}}{serv \mapsto \act{tea}\mpar{x}}{}} (v0);
+\draw (v1) edge[bend left,looseness=0] node {\OTd{\act{serve}\mpar{\mathit{tea}, x}}{}{}} (v0);
 \draw (v0) edge[bend left,looseness=0] node {\OTd{\act{coffee}\mpar{}}{}[m \geq 150]{m \gets m - 150}} (v2);
-\draw (v2) edge[bend left,looseness=0] node {\OTd{\act{serve}\mpar{\mathit{coffee}, x}}{serv \mapsto \act{coffee}\mpar{x}}{}} (v0);
+\draw (v2) edge[bend left,looseness=0] node {\OTd{\act{serve}\mpar{\mathit{coffee}, x}}{}{}} (v0);
 \end{tikzpicture}

### 2021-06-15 2021-Refinement/report.tex
Forgot to add some examples

--- 2021-06-14 2021-Refinement/report.tex
@@
 \section{Introduction}
-The open automata model was originally designed to give the semantic of open pNets \cite{2007.10770}.
+The open automata model is used to give the semantic of open pNets \cite{2007.10770}.
 Open pNets are not petri nets but an intermediate representation used in the VerCors project to perform verification \cite{henrio:01252323}.
 Verification is the process of checking that an implementation satisfies a specification.
-\Ludo{verification is more general than that (or you need to refine specification): checking typing or absence of deadlocks belong to verification}
-Open pNets with the open automaton semantics and equivalence relation introduced in previous work \cite{2007.10770} were sucessfully used to model and verify some properties of applications based on BIP  and GCM \cite{qin:01823507, ameurboulifa:01526055} \Ludo{cite and expand acronym (x2)}.
-However equivalence relations are not always sufficient to perform verification, refinement relations are also used. \Ludo{verification/refinement/equivalence needs to be refined and explained}
-For instance a usecase where open pNet where equivalence is not sufficient can be found  in an article about algorithms fo weak bisimulation on open automata \cite{wang:03126313}.
-
-\Ludo{choose: either 1) you do not refer to open pnets below and explain informally open automata here (why are they useful, what makes them different from automata), or 2) you want to refer to pnets in the following and you explain informally pnets, uatomata and the relation}
-
-The contributions of this article are \Ludo{report?} the definition of composition for open automata without having to define open pNets, and the introduction of several refinement relations for open automata.
-% TODO: expand
+Open pNets with the open automaton semantics and equivalence relation introduced in previous work \cite{2007.10770} were sucessfully used to model and verify BIP and GCM \cite{qin:01823507, ameurboulifa:01526055}.
+However equivalences relations are not always sufficient to perform verification, refinement relations are also used.
+For instance an example of open pNet where equivalence is not sufficient was encountered in an article about algorithms fo weak bisimulation on open automata \cite{wang:03126313}.
+
+The contributions of this article are:
+\begin{enumerate}
+\item The definition of composition for open automata without having to define open pNets.
+\item The characterisation of a composition that doesn't introduce deadlocks.
+\item The introduciton of several refinement relations for open automata that behave nicely with composition.
+\end{enumerate}
 
 % TODO: Related work: thesis
-
-\Ludo{RAPPEL: pour ecrire une intro: 1) on ecrit les contribs, 2) on explique avant les termeis techniques pour que le lecteur comprenne les contribs, 3) quand on a quasi fini le reste on ecrit le plan.
-ON peut commencer 1 et 2 un peu tot meme si il faut rediger le tout assez tard: on peut pas ecrire proprement un article sans avoir en tete les contribs de celui ci}
 
@@
 In Section \ref{sec:def} we give a clean and up to date definition of open automata.
-In Section \ref{sec:comp} we define their composition without requiring the use of open pNets \Ludo{does this mean that previous definitions were using open pnets?
-this might be clarified in contributions but when you redo a definition you must highlight why a new definition was necessary}.
-In Section \ref{sec:proofelts} we adapt several standard properties that we use in the definition of refinement relation from LTS to open automata.
-After that Section \ref{sec:prelref} is dedicated to progressively build a refinement relation and explain the elements of this construction.
+In Section \ref{sec:comp} we define their composition without requiring the use of open pNets.
+In Section \ref{sec:proofelts} we adapt the standard properties related to refinement relation from LTS to open automata.
+After that Section \ref{sec:prelref} is dedicated to progressively build a refinement relation.
 Section \ref{sec:refinement} introduces and analyses the refinement relation on open automata.
-Finally Section \ref{sec:ccl} recapitulates the contribution and presents the work left.
+Finally Section \ref{sec:ccl} recapitulates the contribution and present the work left.
 
@@
 Families of values, or equivalently maps will be noted \(\mset{i \mapsto x_i}{i \in I}\), \(\mset{i \gets x_i}{i \in I}\) or \(x_i^{i \in I}\).
-The latter can only be used if there is a generating expression\Ludo{c est vrai pour les exemples mais pas pour les defs generiques (OA, bisim, ...): reformuler}; for instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\).
+The latter can only be used if there is a generating expression; for instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\).
 However \(\mbrc{\alpha \mapsto 1, \beta \mapsto 2, \gamma \mapsto 3}\) has no generating expression and is represented here with the finite version of first notation.
@@
 There are several ways of ensuring a union is disjoint, we will indifferently either suppose sets are disjoint or rename conflicting object (useful for variables).
-The disjoint union of two maps \(\varphi: I \to X\) and \(\psi: J \to Y\) with \(I \cap J = \emptyset\) has the following signature \(\varphi \uplus \psi: I \uplus J \to X \cup Y\).
+The disjoint union of two maps \(\varphi: I \to X\) and \(\psi: J \to Y\) with \(I \cap J = \emptyset\) is \(\varphi \uplus \psi: I \uplus J \to X \cup Y\).
 
@@
 
-Notations are parameterised by a term algebra \(\terms\).
+The terms \(\terms\) is a term algebra.
 As any term algebra it has constant symbols with arity, variables, and a typing mechanism to distinguish well-formed and ill-formed terms.
 The action algebra \(\actions\) is another term algebra.
-It can be \Ludo{''can be'' is not much informative} a subset of the terms.
+It can be a subset of the terms.
 The formulas \(\formulas\) are at least the first order formulas over \(\terms\) and \(\actions\).
@@
 The formulas contain at least first order logic terms with an equality relation.
-This equality relation is not necessarily a syntactic equality (\(2 + 2 \neq 4\) with a syntactic equality but it is more expressive to consider that the two terms are equal).
-
-An example of term algebra can be Peano integers (constant zero with arity 0, constant successor function with arity 1 and the variables), the formulas associated can use syntactic equality relation, the sum relation \(\mathit{sum}\mpar{a, b, c}: \text{``}a = b + c\text{"}\), and the product relation \(\mathit{prod}\mpar{a, b, c}: \text{``}a = b \times c\text{"}\).
+This equality relation is not necessarily a syntactic equality (\(2 + 2 \neq 4\) with a syntactic equality).
+
+An example of term algebra can be Peano integers (constant zero with arity 0, constant successor function with arity 1 and the variables), the formulas associated can use syntactic equality relation, the sum relation \(\mathit{sum}\mpar{a, b, c}: \text{``}a = b + c\text{"}\) and the product relation \(\mathit{prod}\mpar{a, b, c}: \text{``}a = b \times c\text{"}\).
 
@@
 The interpretation of terms is supposed to be decidable.
-The satisfiability of formulas might not be decidable nor complete nor consistent,
-but we will consider in the following that they are; this can be achieved by restricting the term algebra to a decidable subset.
+The satisfiability of formulas might not be decidable nor complete nor consistent, however we will pretend like they are because these are really hard problems for logicians that we don't want to deal with.
 For instance a formula with quantifiers on variables might not be provable even if it is true for all values of these variables.
-In practice the formulas will be given to a SMT solver and we cannot always make sure they have all the previous properties but, as soon as the satisfiability is consistent our theory is consistent too.
+In practise the formulas will be given to a SMT solver and we cannot always make sure they have all the previous properties.
 \(\vdash\) can hence be interpreted as an indicator of what is given to the SMT; it separates the external logic and the logic on \(\formulas\).
@@
 This is correct when \(\values \subseteq \rterms\) and we suppose it is the case.
-Otherwise it doesn't invalidates theorems because it can stand as a shorthand for substitution with any term which is interpreted the kept value \Ludo{comprends pas la fin de phrase, anglais?}.
+Otherwise it doesn't invalidates theorems because it can stand as a shorthand for substitution with any term which is interpreted the kept value.
 We suppose that the interpretation of terms is compatible w.r.t.\@ substitution, that is if two terms \(t\), \(t'\) are interpreted with the same value, then replacing \(t\) by \(t'\) in a well-formed expression makes an equivalent well-formed expression.
@@
 The variable names may clash when considering two automata, in this case we suppose that we can still distinguish the variables in the formulas.
-In practice the open automata are used in a toolchain  that guarantees there are no name clash.
-
-The initial valuation is a partial valuation of the variables.
+In practise the open automata are used in a toolchain at a point where what came before guarantees there are no name clash, which is why we make this assumption.
+
+The initial valuation may be a partial valuation of the variables.
 If an undefined variable is set before being read, it behaves like an initially set variable.
 If an undefined variable is not set before being read then its value may be any fixed value.
-When refining \Ludo{bizarre de parler de rafinement ici: phrase a deplacer ou introduire par: Later we will consider refinement of autoamata and ....} the automaton it can be set by the implementation, or it can be left unspecified as a parameter of the automaton (for instance a \(n\) bits register has \(n\) as parameter).
+When refining the automaton it can be set by the implementation, or it can be left unspecified as a parameter of the automaton (for instance a \(n\) bits register has \(n\) as parameter).
 \begin{defi}[Open transition]
-An open transition is a tuple \nmm{\OTg} with \(s, s' \in S\) the source and target states, \(\alpha \in \actions\) the produced action, \(J' \subseteq J\) the holes involved in the transition, \(\beta_j \in \actions\) the actions of the holes, \(g \in \formulas\) the guard and \(\psi: V \to \terms\) the variable assignments.
+An open transition is a tuple \nmm{\OTg} with \(s, s' \in S\) the source and target states, \(\alpha \in \actions\) the produced action, \(J' \subseteq J\) the holes involved in the transition, \(\beta_j \in \actions\) the actions of the holes, \(g \in \formulas\) the guard and \(\psi: V \to \terms\) the variables assignements.
 \end{defi}
@@
 
-The intuition of an open automaton is a partially defined LTS with variables, guards on transitions, and parametrised actions.
-The LTS is partial in the sense that one cn plug an LTS in the hole and the surrounding LTS will react to the actions emitted by the sub-LTS put in the hole.
+The intuition of an open automaton is a partially defined LTS with variables, guards on transitions and parametrised actions.
 Initially the automaton is in the initial state with an extension on all the variables of the initial valuation.
 In any configuration, it can perform effective transitions which source state is the current state and which guard is satisfiable in the current valuation if the holes emit the indicated actions.
-An effective transition is a transition where every variable that is not an automaton variable is instantiated with a value.
-By performing the effective transition, the automaton emits the indicated action and updates its configuration according to the target state and variable assignments.
+An effective transition is a transition where every variable that is not an automaton variable is instanciated with a value.
+By performing the effective transition, the automaton emits the indicated action and updates its configuration according to the target state and variables assignements.
 
@@
 The FH-bisimulation \cite{henrio:01055091} is noted \(\cong\).
-
-\Ludo{here the reader needs either an intuition of the FH bisim or a definition in any case, he needs to know that he will get one or the other and when.
-For example we give below an intuitive definition of the FH bisim based on examples.}
-
-\Ludo{ If you need the notation but the def is not important you can explicitly say that the readers should refer to ??
-for the details of the def, but here I do not believe it is wise OR you could say FH bisim is useless and you do not introduce the notation but you should not use it afterwards (again not adapted I believe)}
 
@@
 The \(\act{accept}\) action is shortened as \(\act{acc}\) in the examples.
-During the synchronised action, the value returned by the first agent is passed to the second agent.
+During the synchronised action, the value returned by first agent is passed to the second agent.
 \begin{exi}[Enable, state-oriented]
@@
 It would have avoided many effective transitions with trivially false guards like the one where \(x \mapsto 1, y \mapsto 2\), which has the guard \(1 = 2\).
-\Ludo{I believe that with the usual definition of the semantics of open automata it is the same ...
-please check: you do all potential transitions with the conditions that x is the same in both.
-In any case as the matching is not linear, the simplification is not obvious}
 
@@
 \end{defi}
-
-The goal of the extractor \(\fvars{t}\) when \(t\) is a transition is to get variables that are unique \Ludo{what do you mean by unique here?} to that transition.
-Other variables like automaton variables are already known at this point so there is no use in getting them \Ludo{this is not clear because I do not know what variables you ``NEED'' to ``GET'' (need and get are strange and vague to me)}.
+The goal of the extractor \(\fvars{t}\) when \(t\) is a transition is to get variables that are unique to that transition.
+Other variables like automaton variables are already known at this point so there is no use in getting them.
 Also the use of this extractor benefits from this exclusion: otherwise there would always be \(\setminus V\) following it to prevent variable shadowing.
-
-\Ludo{is it really variable shadowing?}
-
-\Ludo{you do not necessarily need to explain everything if this is what you need, but you miss an intuition of what this set is}
 
@@
 It is an alternative implementation of the enable operator which is FH-bisimilar to the previous one \cite{henrio:01299562}.
-\Ludo{makes no sense: FH bisimlar is still undefined, neither formally nor informally}
-Note that in this example \(r\) and \(l\) are a hole names and also closed terms: this is a naming conflict, though it is not ambiguous because \(J \cap \rterms = \emptyset\) always holds \Ludo{the intersection is at the same time empty and non-empty, why not use a different value (or underline them) or just say that they are in fact different names though it is easier to read using r and l for both}.
-\Ludo{le probleme ici c est qu on a l impression que tu essayes a la fois d etre tres strict et formel et pas vraiment en meme temps, il faut choisir}
-The variables that are said to be local to a transition are all the unbound variables in the expressions minus the automaton variables.
+Note that in this example \(r\) and \(l\) are a hole names and also closed terms: this is a naming conflict, though it is not ambiguous because \(J \cap \rterms = \emptyset\) always holds.
+The variables local to a transition are all the unbound variables in the expressions minus the automaton variables.
 For instance \(v\) is a variable of the automaton (used in the guard).
 It is not local to the transition.
-\Ludo{je comprends ps cette phrase:} In a run, when taking effective transitions (without local variables), its value is not substituted with a closed term.
+In a run, when taking effective transitions (without local variables), its value is not substituted with a closed term.
 For instance \nmm{\OT{»}{»}{\tau}{\mbrc{l \mapsto \tau}}{v = l \wedge \tau \neq \delta}{\mbrc{}}} is an effective transition generated from the second transition but not \nmm{\OT{»}{»}{\tau}{\mbrc{l \mapsto \tau}}{l = l \wedge \tau \neq \delta}{\mbrc{}}} (result of the forbidden substitution \(v \mapsto l\)).
 
-An  run of this open automaton can be: The automaton in the hole \(l\) emits many actions, this synchronises with the only transition possible at that moment because \(v = l\).
+An imaginary run of this open automaton can be: The automaton in the hole \(l\) emits many actions, this synchronises with the only transition possible at that moment because \(v = l\).
 Then the automaton in hole \(l\) emits a \(\delta\mpar{t}\), this is synchonised with the action that sets \(v \gets r\) and the automata in hole \(r\) must emit a \(\act{acc}\mpar{t}\).
@@
 
-Another  run can be: The automaton in the hole \(l\) emits a sequence of non \(\delta\mpar{t}\) actions so the automaton in the hole \(r\) cannot emit a \(\act{acc}\mpar{t}\) and never runs.
+Another imaginary run can be: The automaton in the hole \(l\) emits a sequence of non \(\delta\mpar{t}\) actions so the automaton in the hole \(r\) cannot emit a \(\act{acc}\mpar{t}\) and never runs.
 \end{exi}
 
-From this point open automata and open transitions are sometimes called automata and transitions for simplicity. % NEED NORMALISATION, LEFT IN CASE OF OMISSION
+From this point open automata and open transitions can be called automata and transitions for simplicity. % NEED NORMALISATION, LEFT IN CASE OF OMISSION
 
 \section{Composition of Open Automata}\label{sec:comp}
-Open automata are partially specified automata, that partiality comes mostly from the holes.
-The interpretation of a hole is an interface with another open automaton, in which we can plug an open automaton. The plugging operation is called composition.
-In this article, composition will only refer to filling holes, other compositions like ``parallel composition" (pure interleaving) are not tackled (but one can define an open automaton that performs the parallel composition of two others).
-The composition of open automata was already implicitly defined by the means of composition on pNets in previous work \cite{henrio:01299562} but never completely formalised on open automata.
+Open automata are partially specified automata, part of that partiality comes from the holes.
+The interpretation of a hole is an interface with another open automaton, in which we can plug an open automaton with an operation called composition.
+In this article, composition will only refer to filling holes, other compositions like ``parallel composition" (pure interleaving) are not tackled.
+The composition of open automata was already implicitely defined by the means of composition on pNets in previous work \cite{henrio:01299562} but never completely formalised on open automata.
 The definition of composition below is a direct translation of what happens with pNets composition without the need of introducing pNets.
 \begin{defi}[Composition of open automata]
-The composition of \(A_c \defobject \OAg[c]\) in the hole \(k \in J_p\) of \(A_p \defobject \OAg[p]\) is an open automaton defined as follows.
+The composition of \(A_c \defobject \OAg[c]\) in the hole \(k \in J_p\) of \(A_p \defobject \OAg[p]\) is
 \begin{align*}
@@
 The action emitted when \(A_c\) makes a transition is sychronised with the action of the hole \(k\) in transitions of \(A_p\) which have it as a hole action (first transition set, \(\alpha_c = \beta_k\)).
-The composition may look like a handshake, with both automata running in parallel (product of states and joint variables) however it is asymmetric because it is the first automaton that decides when the second can evolve, while the first automaton can evolve independently as soon as the hole is not involved in the open transition considered.
+The composition may look like a handshake, with both automata running in parallel (product of states and joint variables) however it is asymmetric because of the second transition set (\(k \notin J'_p\)):
+No transition of \(A_c\) is performed when a transition that do not refer to the hole \(k\) is performed in \(A_p\).
 
 Composition is a complex process that generates big automata with complex and potentially simplifiable transitions.
-However simplification is a hard problem that is not yet automatised on open automata, so from this point the guards and transitions will always be simplified by hand without further explanation.
+However simplification is a hard problem that is not yet automatised on open automata, so from this point the guards and transitions will always be simplified by hand without further explaination.
 An example of composition can be found in Appendix \ref{apx:composition}.
@@
 Even if an automaton is composed in two distinct holes it does not share its variables, each composition makes the cartesian product of states and a disjoint union of the variables.
-In practice, variables may have to be renamed.
+In practise, variables may have to be renamed.
 
@@
 However it does not capture the removal of holes because other issues arise when trying to both add and remove holes.
-
-Examples of application of the different refinement relations are given in Appendix \ref{apx:refrel}.% TODO: Maybe put them here, not in appendix
+\begin{exi}{Example of hole-equal simulation}
+\begin{figure}
+\centering
+\input{parallel_comp.tex}
+\vrule
+\input{n_control_switch.tex}
+\caption{On the left: Parallel composition operator; On the right: n control switches automaton}
+\label{fig:hisim}
+\end{figure}
+Figure \ref{fig:hisim} introduces two related open automata with same holes \(\mbrc{l, r}\).
+The automaton on the left is a parallel composition: any hole can perform actions at any time, the actions are passed unmodified and no synchronisation is performed.
+The automaton on the right is a sequential composition with \(n\) control switches: a hole performs a sequence of actions then the other does, there are \(n\) seqences of a single automaton doing actions without the other performing some.
+
+Intuitively the right automaton is a refinement of the left automaton because the left automaton is what happens when there was no bound \(n\) in the right automaton.
+\[ R \defobject \mbrc{\mpar{l, ||} \mapsto \top, \mpar{r, ||} \mapsto \top} \]
+\(R\) is a hole-identical simulation of \(n\) control switches by parallel composition.
+There are enough examples of proofs of refinement in this article for the reader to be able to prove it as an exercise.
+\end{exi}
+\begin{exi}{Example of hole-subset simulation}
+Example of Appendix \ref{apx:composition} can be reused here.
+The automaton on Figure \ref{fig:tlf} is a refinement of the one on Figure \ref{fig:tls} by limited composition correctness (Proposition \ref{prop:cc'}).
+
+It is a simplified version of the motivation for making a refinement relation, which is the traffic light system in an article about weak-bisimulation \cite{wang:03126313}.
+It had to be modified because here the simulation is a strong-simulation (no silent actions).
+\end{exi}
+\begin{exi}{Example of hole-superset simulation}
+\begin{figure}
+\centering
+\input{Vending_machine.tex}
+\hrule
+\input{Open_vending_machine.tex}
+\caption{On the top: Vending machine; On the bottom: Open vending machine}
+\label{fig:ovm}
+\end{figure}
+% TODO: Explain example and adding holes
+\end{exi}
 \begin{thm} A hole-\(\triangle\) simulation is a pre-simulation. \end{thm}
@@
 However this doesn't implies \(A \leq_{\bigcup_{i \in I} J_{Bi}} C\), it has to be checked separately.
-% TODO: maybe add an example here
-
+\begin{exi}
+\begin{figure}
+\centering
+\input{identity.tex}
+\vrule
+\input{any.tex}
+\vrule
+\input{handshake_comp}
+\caption{On the left: Generic identity on holes; On the middle: Any action automaton; On the right: Handshake composition.}
+\label{fig:sevpathref}
+\end{figure}
+We have two refinement path when \(h\) is replaced by \(l\) and by \(r\) in Figure \ref{fig:sevpathref}: the parallel composition (left of Figure \ref{fig:hisim}) is a refinement of the identity on holes (right of Figure \ref{fig:sevpathref}), which is a refinement of the handshake composition (right of Figure \ref{fig:sevpathref}).
+However we do not have the parallel composition being a refinement of the handshake composition looking at \(\mbrc{l, r}\).
+
+The example also shows a property worth mentionning.
+The holes not looked at (or untracked) are equivalent to having the automaton on the middle of Figure \ref{fig:sevpathref} composed.
+Actually all the previous refinement are both ways: we can compose the Any action automaton in hole \(r\) of the parallel composition to get the other way of the refinement with the identity on holes by compositon correctness, and we transform the transition from the identity on holes into the one of the handshake composition by hole-superset refinement.
+\end{exi}
 The other interesting properties left to check are correctness w.r.t.\@ composition, context refinement, composition congruence and compatibility with FH-bisimulation.
@@
 The requirements of FH-bisimulation are strictly stronger than the open automata refinement so using transitivity is sufficient.
-
-% TODO HERE: What happens on untracked holes (untracked holes equivalent behaviour => free variables; some sort of daisy equivalence)
 
@@
 
-\section{Examples of hole-\(\triangle\) simulations}\label{apx:refrel}
-
-\subsection{Example of hole-equal simulation}
-\begin{exi}
-\begin{figure}
-\centering
-\input{parallel_comp.tex}
-\vrule
-\input{n_control_switch.tex}
-\caption{On the left: Parallel composition operator; On the right: n control switches automaton}
-\label{fig:hisim}
-\end{figure}
-Figure \ref{fig:hisim} introduces two related open automata with same holes \(\mbrc{l, r}\).
-The automaton on the left is a parallel composition: any hole can perform actions at any time, the actions are passed unmodified and no synchronisation is performed.
-The automaton on the right is a sequential composition with \(n\) control switches: a hole performs a sequence of actions then the other does, there are \(n\) seqences of a single automaton doing actions without the other performing some.
-
-Intuitively the right automaton is a refinement of the left automaton because the left automaton is what happens when there was no bound \(n\) in the right automaton.
-\[ R \defobject \mbrc{\mpar{l, ||} \mapsto \top, \mpar{r, ||} \mapsto \top} \]
-\(R\) is a hole-identical simulation of \(n\) control switches by parallel composition.
-There are enough examples of proofs of refinement in this article for the reader to be able to prove it as an exercise.
-\end{exi}
-
-\subsection{Example of hole-subset simulation}
-Example of Appendix \ref{apx:composition} can be reused here.
-The automaton on Figure \ref{fig:tlf} is a refinement of the one on Figure \ref{fig:tls} by limited composition correctness (Proposition \ref{prop:cc'}).
-
-It is a simplified version of the motivation for making a refinement relation, which is the traffic light system in an article about weak-bisimulation \cite{wang:03126313}.
-It had to be modified because here the simulation is a strong-simulation (no silent actions).
-
-\subsection{Example of hole-superset simulation}
-% TODO: vending machine of the presentation + money module
-
 \section{Proofs of properties for hole-\(\triangle\) simulation}

### 2021-06-15 2021-Refinement/report.tex

--- 2021-06-15 2021-Refinement/report.tex
@@
 
-\Ludo{choose: either 1) you do not refer to open pnets below and explain informally open automata here (why are they useful, what makes them different from automata), or 2) you want to refer to pnets in the following and you explain informally pnets, uatomata and the relation}
-
-The contributions of this article are \Ludo{report?} the definition of composition for open automata without having to define open pNets, and the introduction of several refinement relations for open automata.
-% TODO: expand
+The contributions of this report are:
+\begin{enumerate}
+\item Formalisation of composition for open automata.
+\item The characterisation of a composition that doesn't introduce deadlocks.
+\item The introduciton of several refinement relations for open automata that behave nicely with composition.
+\end{enumerate}
 

### 2021-06-15 2021-Refinement/report.tex
Solving some thingies

@@
 Open pNets are not petri nets but an intermediate representation used in the VerCors project to perform verification \cite{henrio:01252323}.
-Verification is the process of checking that an implementation satisfies a specification.
-\Ludo{verification is more general than that (or you need to refine specification): checking typing or absence of deadlocks belong to verification}
-Open pNets with the open automaton semantics and equivalence relation introduced in previous work \cite{2007.10770} were sucessfully used to model and verify some properties of applications based on BIP and GCM \cite{qin:01823507, ameurboulifa:01526055} \Ludo{cite and expand acronym (x2)}.
-However equivalence relations are not always sufficient to perform verification, refinement relations are also used. \Ludo{verification/refinement/equivalence needs to be refined and explained}
-For instance a usecase where open pNet where equivalence is not sufficient can be found in an article about algorithms fo weak bisimulation on open automata \cite{wang:03126313}.
+This model is based around a hierarchical composition of generalised automata.
+Verification is the process of checking properties on a description in a specific model (for instance an automaton).
+This properties can be for instance being in some type or being deadlock free (a deadlock is an unintended state where no further action is possible).
+Open pNets with the open automaton semantics and equivalence relation introduced in previous work \cite{2007.10770} were sucessfully used to model and verify some properties of applications \cite{qin:01823507, ameurboulifa:01526055} based on BIP (Behaviour-Interaction-Priority) \cite{basu:hal-00722395} and GCM (Grid Component Model) \cite{baude:inria-00323919}.
+However equivalence relations are not always sufficient to perform verification, refinement relations are also used.
+A refinement is the verification that an implementation satisfies a specification, whereas an equivalence would check that their behaviours are the same.
+For instance a usecase on open pNet where equivalence is not sufficient can be found in an article about algorithms fo weak bisimulation on open automata \cite{wang:03126313}.
 
@@
 \begin{enumerate}
-\item Formalisation of composition for open automata.
+\item Formalisation of composition for open automata without requiring open pNets.
 \item The characterisation of a composition that doesn't introduce deadlocks.
@@
 \end{enumerate}
-
 % TODO: Related work: thesis
-
-\Ludo{RAPPEL: pour ecrire une intro: 1) on ecrit les contribs, 2) on explique avant les termeis techniques pour que le lecteur comprenne les contribs, 3) quand on a quasi fini le reste on ecrit le plan.
-ON peut commencer 1 et 2 un peu tot meme si il faut rediger le tout assez tard: on peut pas ecrire proprement un article sans avoir en tete les contribs de celui ci}
 
@@
 Families of values, or equivalently maps will be noted \(\mset{i \mapsto x_i}{i \in I}\), \(\mset{i \gets x_i}{i \in I}\) or \(x_i^{i \in I}\).
-The latter can only be used if there is a generating expression\Ludo{c est vrai pour les exemples mais pas pour les defs generiques (OA, bisim, ...): reformuler}; for instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\).
+The latter can only be used if there is a generating expression\Ludo{c est vrai pour les exemples mais pas pour les defs generiques (OA, bisim, ...): reformuler}\Quentin{Je pense que c'est aussi vrai pour les defs génériques, on définit une famille à l'aide d'une expression génératrice, par exemple \(\mpar{\beta_j}_{j \in J}\) est en réalité \(j \mapsto \beta_j\); une fonction est une expression génératrice}; for instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\).
 However \(\mbrc{\alpha \mapsto 1, \beta \mapsto 2, \gamma \mapsto 3}\) has no generating expression and is represented here with the finite version of first notation.
@@
 The action algebra \(\actions\) is another term algebra.
-It can be \Ludo{''can be'' is not much informative} a subset of the terms.
+It can be \Ludo{''can be'' is not much informative}\Quentin{Intended use, it is not mandatory} a subset of the terms.
 The formulas \(\formulas\) are at least the first order formulas over \(\terms\) and \(\actions\).
@@
 This is correct when \(\values \subseteq \rterms\) and we suppose it is the case.
-Otherwise it doesn't invalidates theorems because it can stand as a shorthand for substitution with any term which is interpreted the kept value \Ludo{comprends pas la fin de phrase, anglais?}.
+Otherwise it doesn't invalidates theorems because it can stand as a shorthand for substitution with any term which has the kept value as an interpretation\Ludo{comprends pas la fin de phrase, anglais?}\Quentin{Il manquait des mots}.
 We suppose that the interpretation of terms is compatible w.r.t.\@ substitution, that is if two terms \(t\), \(t'\) are interpreted with the same value, then replacing \(t\) by \(t'\) in a well-formed expression makes an equivalent well-formed expression.
@@
 If an undefined variable is not set before being read then its value may be any fixed value.
-When refining \Ludo{bizarre de parler de rafinement ici: phrase a deplacer ou introduire par: Later we will consider refinement of autoamata and ....} the automaton it can be set by the implementation, or it can be left unspecified as a parameter of the automaton (for instance a \(n\) bits register has \(n\) as parameter).
+When we will introduce refinements in Section \ref{sec:prelref}, setting an undefined variable will be considered a valid refinement, for instance a \(5\) bits register is a particular \(n\) bits register.
 \begin{defi}[Open transition]
@@
 
-\Ludo{here the reader needs either an intuition of the FH bisim or a definition in any case, he needs to know that he will get one or the other and when.
-For example we give below an intuitive definition of the FH bisim based on examples.}
-
-\Ludo{ If you need the notation but the def is not important you can explicitly say that the readers should refer to ??
-for the details of the def, but here I do not believe it is wise OR you could say FH bisim is useless and you do not introduce the notation but you should not use it afterwards (again not adapted I believe)}
-
 The FH-bisimulation is currently the only equivalence relation on open automata.
+The definition is not important, but the interested reader can check the article cited.
 \end{noti}
@@
 please check: you do all potential transitions with the conditions that x is the same in both.
-In any case as the matching is not linear, the simplification is not obvious}
+In any case as the matching is not linear, the simplification is not obvious}\Quentin{Same behaviour as here with the standard definition: RR-9177, sec 5.2}
 
@@
 \end{defi}
-
-The goal of the extractor \(\fvars{t}\) when \(t\) is a transition is to get variables that are unique \Ludo{what do you mean by unique here?} to that transition.
-Other variables like automaton variables are already known at this point so there is no use in getting them \Ludo{this is not clear because I do not know what variables you ``NEED'' to ``GET'' (need and get are strange and vague to me)}.
+The goal of the extractor \(\fvars{t}\) when \(t\) is a transition is to get variables that are only present in that transition.
+Also transition variables sets are disjoint from one transition to another.
+Other variables like automaton variables are already known at this point so there is no use in getting their name again.
 Also the use of this extractor benefits from this exclusion: otherwise there would always be \(\setminus V\) following it to prevent variable shadowing.
 
-\Ludo{is it really variable shadowing?}
-
-\Ludo{you do not necessarily need to explain everything if this is what you need, but you miss an intuition of what this set is}
+\Ludo{is it really variable shadowing?}\Quentin{I don't know if the term is the same in math}
+
+\Ludo{you do not necessarily need to explain everything if this is what you need, but you miss an intuition of what this set is}\Quentin{I don't know what else I could say to give the intuition, all elements are here, in my opinion, the only thing left to build the intuition is an example}
 
@@
 \begin{align*}
-	\OT{»}{»}{x}{\mbrc{l \mapsto x}}{v = l \wedge x \neq \delta}{\mbrc{}} &&
-	\OT{»}{»}{\tau}{\mbrc{l \mapsto \delta\mpar{x}, r \mapsto \act{acc}\mpar{y}}}{v = l \wedge x = y}{\mbrc{v \gets r}} &&
-	\OT{»}{»}{x}{\mbrc{r \mapsto x}}{v = r}{\mbrc{}}
-\end{align*}
-It is an alternative implementation of the enable operator which is \Ludo{FH-bisimilar}{makes no sense: FH bisimlar is still undefined, neither formally nor informally} to the previous one \cite{henrio:01299562}.
-Note that in this example \(r\) and \(l\) are a hole names and also closed terms: this is a naming conflict, though it is not ambiguous because \(J \cap \rterms = \emptyset\) always holds \Ludo{}{the intersection is at the same time empty and non-empty, why not use a different value (or underline them) or just say that they are in fact different names though it is easier to read using r and l for both}.
-\Ludo{le probleme ici c est qu on a l impression que tu essayes a la fois d etre tres strict et formel et pas vraiment en meme temps, il faut choisir}
+	\OT{»}{»}{x}{\mbrc{l \mapsto x}}{v = L \wedge x \neq \delta}{\mbrc{}} &&
+	\OT{»}{»}{\tau}{\mbrc{l \mapsto \delta\mpar{x}, r \mapsto \act{acc}\mpar{y}}}{v = L \wedge x = y}{\mbrc{v \gets R}} &&
+	\OT{»}{»}{x}{\mbrc{r \mapsto x}}{v = R}{\mbrc{}}
+\end{align*}
+It is an alternative implementation of the enable operator which is FH-bisimilar\Ludo{makes no sense: FH bisimlar is still undefined, neither formally nor informally}\Quentin{I can remove this sentence, it adds nothing} to the previous one \cite{henrio:01299562}.
 The variables that are said to be local to a transition are all the unbound variables in the expressions minus the automaton variables.
@@
 It is not local to the transition.
-\Ludo{In a run,}{je comprends ps cette phrase:} when taking effective transitions (without local variables), its value is not substituted with a closed term.
-For instance \nmm{\OT{»}{»}{\tau}{\mbrc{l \mapsto \tau}}{v = l \wedge \tau \neq \delta}{\mbrc{}}} is an effective transition generated from the second transition but not \nmm{\OT{»}{»}{\tau}{\mbrc{l \mapsto \tau}}{l = l \wedge \tau \neq \delta}{\mbrc{}}} (result of the forbidden substitution \(v \mapsto l\)).
-
-An run of this open automaton can be: The automaton in the hole \(l\) emits many actions, this synchronises with the only transition possible at that moment because \(v = l\).
-Then the automaton in hole \(l\) emits a \(\delta\mpar{t}\), this is synchonised with the action that sets \(v \gets r\) and the automata in hole \(r\) must emit a \(\act{acc}\mpar{t}\).
+When taking effective transitions, its value is not substituted with a closed term.
+For instance \nmm{\OT{»}{»}{\tau}{\mbrc{l \mapsto \tau}}{v = L \wedge \tau \neq \delta}{\mbrc{}}} is an effective transition generated from the second transition but not \nmm{\OT{»}{»}{\tau}{\mbrc{l \mapsto \tau}}{L = L \wedge \tau \neq \delta}{\mbrc{}}} (result of the forbidden substitution \(v \mapsto L\)).
+
+An run of this open automaton can be: The automaton in the hole \(l\) emits many actions, this synchronises with the only transition possible at that moment because \(v = L\).
+Then the automaton in hole \(l\) emits a \(\delta\mpar{t}\), this is synchonised with the action that sets \(v \gets R\) and the automata in hole \(r\) must emit a \(\act{acc}\mpar{t}\).
 Finally the automaton in the hole \(r\) emits any sequence of actions.
@@
 \end{exi}
-
 From this point open automata and open transitions are sometimes called automata and transitions for simplicity. % NEED NORMALISATION, LEFT IN CASE OF OMISSION
@@
 For example if we are interested in producing the same sequences of actions as another automaton we may want to use trace set inclusion as a refinement.
-Here the main expected properties are related to composition and action refinement. % LATER: explain action refinement here or remove if not tackled
+In this section we will present the main expected properties, which are related to composition.
 Because of composition, a relation as strong as simulation must be used.
-
-\Ludo{New}{je suggere un paragraphe du style}
-In this section we present a set of properties that can be desirable for a refinement relation.
-We reach a point where we state a property that guarantees that the refinement does not create additional deadlock.
-Unfortunately, in the general case, this property is contradictory with the other ones, this is why we restrict the general composition defined before so that we only consider a composition to be valid if it does not create deadlocks.
-With this new condition on validity of composition we are able to define in the next sections a refinement relation where most of the properties of interest are satisfied.
 
@@
 The first is between states of two specific automata (\(R \subseteq S_1 \times S_2\)), the second is between automata (\(A_1 \leq A_2\)).
-\Ludo
-{Generally the second is implicit because its definition is always \(\exists R \subseteq S_1 \times S_2, P\mpar{R}\) with \(P\) a property, and only talking about \(R\) and \(P\) is sufficient.}{je comprends pas cette phrase}
+Generally the second relation is implicit because its definition is always \(\exists R \subseteq S_1 \times S_2, P\mpar{R}\) with \(P\) a property on the relation on states, so only talking about \(R\) by defining \(P\) is sufficient.\Ludo{je comprends pas cette phrase}\Quentin{Est-ce mieux?}
 However later on in this article we will define more complex relations on automata so we clarify the distinction now.
+
 A relation of second kind will be called ``relation on automata" whereas a relation of the first kind is called ``relation on configurations" as defined below.
@@
 \end{defi}
-The important properties we consider for the relation on automata are:
+In this section we give properties on refinement relations, both on the relations on configurations and on the relation on automata.
+When relating two automata \(A_1 \mathrel{\mathcal{R}} A_2\) or their configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\), \(A_1\) will be called the implementation and \(A_2\) the specification.
+
+For the relation on automata, the important properties we consider are:
 \begin{defi} A relation on open automata \(\leq\) is
@@
 Reflexivity, transitivity and preorder are classical properties on relations.
-Correctness w.r.t.\@ composition means that every composition is considered a refinement. \Ludo{problem}{ you have not yet said that your relation was a refinement!}
+Correctness w.r.t.\@ composition means that every composition is considered a refinement.
 This property captures the expected behaviour of a refinement relation on a compositional structure like the open automata.
@@
 This property is useful if we want to characterise the kind of operations that can generate any refined automaton starting from the specification.
-\Ludo{}{I do not understand this: what is the domain of the valuation?}
-We won't have it because extending the domain of the initial valuation will be a refinement which can't be expressed with composition.
+We won't have it because extending the domain of definition of the initial valuation will be a refinement which can't be expressed with composition.
 Yet a ``completeness w.r.t.\@ some set of operations" is still a strong and interesting property.
@@
 
-\Ludo{ }{I do not understand the english + too many important properties you should give a hierarchy or at least find a better transition}
-The important properties we consider for the relation on states are being a simulation and the prevention of deadlocks as defined in the following definitions.
+\Ludo{I do not understand the english + too many important properties you should give a hierarchy or at least find a better transition}\Quentin{Important properties not on the same object, this is now underlined by moving the object at the start of the sentences}
+For the relation on states, the important properties we consider are being a pre-simulation and prevent the introduction of deadlocks as defined in the following.
 \begin{defi}[Pre-simulation]
@@
 Here we assume that one of the related open automata can be obtained by composing an open automaton in a hole, open automaton which can have holes itself.
-This implies that there is no relation between \Ludo{their}{whose?
-refine} holes, for instance composing \(A_i\) in \(j_i\) (\(1 \leq i \leq n\)) of \(A_0\) gives the set of holes \(J \defobject \mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}\) that is neither subset nor superset of \(J_0\).
+This implies that there is no relation between the related automata's holes, for instance composing \(A_i\) in \(j_i\) (\(1 \leq i \leq n\)) of \(A_0\) gives the set of holes \(J \defobject \mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}\) that is neither subset nor superset of \(J_0\).
 Yet we still assume that in holes with the same name, the same open automaton will be composed.
@@
 They can arise unpredictably when parallelism is involved (which is the case in our composition) and they generally break the intended behaviour of a system.
-By preventing them we \Ludo{could}{This seems to say that it is useless to prevent them} hope that the refinement preserves some liveness properties.
+By preventing them we could\Ludo{This seems to say that it is useless to prevent them} also\Quentin{Is it better with this additionnal word?} hope that the refinement preserves some liveness properties.
 \begin{defi}[Deadlock prevention, intuitive definition]
@@
 \defitem It is a pre-simulation;
-\defitem If from related states, there is a possible transition in the \Ludo{specification}{I do not believe specification has been defined nor implementation}, then there is \Ludo{a pair of matching transition}{A matching transition in the IMPLEMENTATION}:
+\defitem If from related states, there is a possible transition in the specification, then there is a pair of possible matching transitions from both automata:
 \begin{multline*}
@@
 \end{defi}
-Actually, this requirement prevents the presence of deadlock state in the first automaton if there is a related non-deadlock state in the second by \Ludo{contraposition}{The contraposition is too tricky for me: are you sure?}.
-Additionally, the transition preventing \Ludo{the deadlock}{in the implementation?
-how can it be the same?why is there a single one?
-this sentence makes no sense to me} has to be an existing transition in the specification.
-This is because a valid transition unmatched in the specification \Ludo{is not a deadlock}{how can a transition be a deadlock? I am completely lost}, yet \Ludo{we do not want it}{too informal}.
-The \Ludo{direct formulation}{usually you say ``the direct'' when the property seems to be defined negatively which is syntactically not the case here: you should explain or remove the remark} of the property would also have required the unintuitive quantification on a possibly empty set of transition to state that they are impossible.
-The two previous reasons motivated the formulation in contraposed form.
-
+Actually, this requirement prevents the presence of deadlocks in the first automaton if there is a related non-deadlock configuration in the second by contraposition\Ludo{The contraposition is too tricky for me: are you sure?}\Quentin{I am, I want to say that this property is in contraposition form because the formula is not exactly what I pretend it is right there.}.
+Two reasons motivated the formulation in contraposed form:
+\begin{itemize}
+\item We require a pair of matching transitions from both automata because we do not want a transition in the implementation making a configuration not a deadlock but this transition cannot be taken from the related configuration of the specification.
+\item The non contraposed formulation of the property would have required the unintuitive quantification on a possibly empty set of transition to state that they are not satisfied.
+\end{itemize}
+\Quentin{Déplacé}\Ludo{je suggere un paragraphe du style}
+Unfortunately, in the general case, this property is contradictory with the other ones, this is why we restrict the general composition defined before so that we only consider a composition to be valid if it does not create deadlocks.
+With this new condition on validity of composition we are able to define in the next sections a refinement relation where most of the properties of interest are satisfied.
+\Quentin{Il faut discuter de tout ça, je pense qu'il y a une incompréhension}
+
+\label{reply}
 ``Deadlock prevention" conflicts with all the properties where composition is involved (for instance ``composition correctness") by disallowing some unwanted cases where an automaton in a hole cannot produce any action that any out-transition expects.
@@
 
-\Ludo{Here or before you should explain exactly WHAT YOU WANT: I do not know which are the required property which you will achieve which are incompatible, or state that you will now investigate each property and state whether it is desired / achievable/ compatible with the others: without this analysis the reader is lost}{}
+\Ludo{Here or before you should explain exactly WHAT YOU WANT: I do not know which are the required property which you will achieve which are incompatible, or state that you will now investigate each property and state whether it is desired / achievable/ compatible with the others: without this analysis the reader is lost}\Quentin{\ref{reply}}
 
@@
 \item[\goal{2}:] Let \(\sigma: V \uplus V_1 \uplus \fvars{t} \to \values\).
-	We rename some variables in the input domain of \(\sigma\) to get \(\nu: \fvars{t_1} \to \values\).
+	We rename some variables in the domain of definition of \(\sigma\) to get \(\nu: \fvars{t_1} \to \values\).
 	We use \(\nu\) to prove \goal{2}, get the left side of the implication as an hypothesis and break the right side of the implication:

### 2021-06-15 2021-Refinement/report.tex
All todos resolved except conclusion

@@
 ``Deadlock prevention" conflicts with all the properties where composition is involved (for instance ``composition correctness") by disallowing some unwanted cases where an automaton in a hole cannot produce any action that any out-transition expects.
-In particular filling a hole with the deadlock automaton (only one state without out-transitions) is not considered a refinement for a deadlock reducing relation.
-
-\Ludo{Here or before you should explain exactly WHAT YOU WANT: I do not know which are the required property which you will achieve which are incompatible, or state that you will now investigate each property and state whether it is desired / achievable/ compatible with the others: without this analysis the reader is lost}\Quentin{\ref{reply}}
-
-A way to solve \Ludo{these conflicts}{which conflict?
+In particular filling a hole with the deadlock automaton (only one state without out-transitions) is not considered a refinement for a deadlock preventing relation but any other property about composition would require it being a refinement.
+
+\Ludo{Here or before you should explain exactly WHAT YOU WANT: I do not know which are the required property which you will achieve which are incompatible, or state that you will now investigate each property and state whether it is desired / achievable/ compatible with the others: without this analysis the reader is lost}
+\Quentin{\ref{reply}}
+
+A way to solve these conflicts\Ludo{which conflict?
 can be clarified by answering the previous remark} is to characterise a composition that do not introduce deadlocks, which will be used instead of the composition introduced earlier.
@@
 However it does not capture the removal of holes because other issues arise when trying to both add and remove holes.
-\begin{exi}{Example of hole-equal simulation}
+\begin{exi}[Example of hole-equal simulation]
 \begin{figure}
@@
 \end{exi}
-\begin{exi}{Example of hole-subset simulation}
+\begin{exi}[Example of hole-subset simulation]
 Example of Appendix \ref{apx:composition} can be reused here.
@@
 \end{exi}
-\begin{exi}{Example of hole-superset simulation}
+\begin{exi}[Example of hole-superset simulation]
 \begin{figure}
@@
 \end{figure}
-% TODO: Explain example and adding holes
+Figure \ref{fig:ovm} introduces two related open automata with same states and transitions except for hole actions.
+Both automata are vending machine: Money is introduced while in state \(I\), accumulating in the money variable \(m\), when there are enough money a coffe or a tea can be ordered by taking the transitions to the states \(C\) or \(T\) and money is decreased, then the drink is served by taking the transition back to state \(I\).
+
+The automaton on the bottom is a refinement of the automaton on the top using hole-superset simulation.
+The relation on states is the same as the one for reflexivity.
+Intuitively the automaton on the bottom binds some variables to action produced by the holes, the automaton is no more free to take a transition some hole is not able to perform.
+For instace if the automaton in the hole \(mon\) can only perform \(\act{credit}\mpar{100}\) then after the composition, the automaton on the bottom should be a refinement of the one on the top.
+Actually after such a composition it is still in hole-superset simulation with the top automaton by Proposition \ref{prop:cc'}.
 \end{exi}

### 2021-06-16 2021-Refinement/report.tex
Better fixes

@@
 In Section \ref{sec:def} we give a clean and up to date definition of open automata.
-In Section \ref{sec:comp} we define their composition without requiring the use of open pNets \Ludo{does this mean that previous definitions were using open pnets?
-this might be clarified in contributions but when you redo a definition you must highlight why a new definition was necessary}.
-In Section \ref{sec:proofelts} we adapt several standard properties that we use in the definition of refinement relation from LTS to open automata.
+In Section \ref{sec:comp} we define their composition without requiring the use of open pNets \Ludo{}{does this mean that previous definitions were using open pnets?
+this might be clarified in contributions but when you redo a definition you must highlight why a new definition was necessary}\Quentin{}{Yes, composition of open automata was composition of the open pNets generating them, the necessity is as stated, being independant from open pNets}.
+In Section \ref{sec:proofelts} we adapt to open automata several standard properties from refinement relations on LTS.
 After that Section \ref{sec:prelref} is dedicated to progressively build a refinement relation and explain the elements of this construction.
@@
 Families of values, or equivalently maps will be noted \(\mset{i \mapsto x_i}{i \in I}\), \(\mset{i \gets x_i}{i \in I}\) or \(x_i^{i \in I}\).
-The latter can only be used if there is a generating expression\Ludo{c est vrai pour les exemples mais pas pour les defs generiques (OA, bisim, ...): reformuler}\Quentin{Je pense que c'est aussi vrai pour les defs génériques, on définit une famille à l'aide d'une expression génératrice, par exemple \(\mpar{\beta_j}_{j \in J}\) est en réalité \(j \mapsto \beta_j\); une fonction est une expression génératrice}; for instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\).
+The latter can only be used if there is a \Ludo{generating expression}{c'est vrai pour les exemples mais pas pour les defs generiques (OA, bisim, ...): reformuler}\Quentin{}{Je pense que c'est aussi vrai pour les defs génériques, on définit une famille à l'aide d'une expression génératrice, par exemple \(\mpar{\beta_j}_{j \in J}\) est en réalité \(j \mapsto \beta_j\); une fonction est une expression génératrice}; for instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\).
 However \(\mbrc{\alpha \mapsto 1, \beta \mapsto 2, \gamma \mapsto 3}\) has no generating expression and is represented here with the finite version of first notation.
@@
 The action algebra \(\actions\) is another term algebra.
-It can be \Ludo{''can be'' is not much informative}\Quentin{Intended use, it is not mandatory} a subset of the terms.
+It \Ludo{can be}{not much informative}\Quentin{}{Intended use, it is not mandatory} a subset of the terms.
 The formulas \(\formulas\) are at least the first order formulas over \(\terms\) and \(\actions\).
@@
 This is correct when \(\values \subseteq \rterms\) and we suppose it is the case.
-Otherwise it doesn't invalidates theorems because it can stand as a shorthand for substitution with any term which has the kept value as an interpretation\Ludo{comprends pas la fin de phrase, anglais?}\Quentin{Il manquait des mots}.
+Otherwise it doesn't invalidates theorems because it can stand as a shorthand for substitution with any term which has the kept value as an interpretation.
 We suppose that the interpretation of terms is compatible w.r.t.\@ substitution, that is if two terms \(t\), \(t'\) are interpreted with the same value, then replacing \(t\) by \(t'\) in a well-formed expression makes an equivalent well-formed expression.
@@
 It would have avoided many effective transitions with trivially false guards like the one where \(x \mapsto 1, y \mapsto 2\), which has the guard \(1 = 2\).
-\Ludo{I believe that with the usual definition of the semantics of open automata it is the same ...
+\Ludo{}{I believe that with the usual definition of the semantics of open automata it is the same ...
 please check: you do all potential transitions with the conditions that x is the same in both.
-In any case as the matching is not linear, the simplification is not obvious}\Quentin{Same behaviour as here with the standard definition: RR-9177, sec 5.2}
+In any case as the matching is not linear, the simplification is not obvious}\Quentin{}{Same behaviour as here with the standard definition: RR-9177, sec 5.2}
 
@@
 
-\Ludo{is it really variable shadowing?}\Quentin{I don't know if the term is the same in math}
-
-\Ludo{you do not necessarily need to explain everything if this is what you need, but you miss an intuition of what this set is}\Quentin{I don't know what else I could say to give the intuition, all elements are here, in my opinion, the only thing left to build the intuition is an example}
+\Ludo{}{is it really variable shadowing?}\Quentin{}{I don't know if the term is the same in math}
+
+\Ludo{}{you do not necessarily need to explain everything if this is what you need, but you miss an intuition of what this set is}\Quentin{}{I don't know what else I could say to give the intuition, all elements are here, in my opinion, the only thing left to build the intuition is an example}
 
@@
 \end{align*}
-It is an alternative implementation of the enable operator which is FH-bisimilar\Ludo{makes no sense: FH bisimlar is still undefined, neither formally nor informally}\Quentin{I can remove this sentence, it adds nothing} to the previous one \cite{henrio:01299562}.
+It is an alternative implementation of the enable operator which is \Ludo{FH-bisimilar}{makes no sense: FH bisimlar is still undefined, neither formally nor informally} to the previous one \cite{henrio:01299562}.\Quentin{}{I can remove this sentence, it adds nothing}
 The variables that are said to be local to a transition are all the unbound variables in the expressions minus the automaton variables.
@@
 \section{Properties of a refinement relation for Open Automata}\label{sec:proofelts}
-There are several properties we may expect from a refinement relation.
-Depending on these properties, different kinds of refinement can be used.
+We want to define a refinement relation on open automata, this refinement relation is expected to have some properties to be of any use.
+In this section we list and adapt to open automata the properties expected from a refinement relation.
+
+There are several kind of refinement relation depending on the properties we want.
 For example if we are interested in producing the same sequences of actions as another automaton we may want to use trace set inclusion as a refinement.
-In this section we will present the main expected properties, which are related to composition.
+The main expected properties here are the standard properties on relations and the ones related to composition.
 Because of composition, a relation as strong as simulation must be used.
@@
 The first is between states of two specific automata (\(R \subseteq S_1 \times S_2\)), the second is between automata (\(A_1 \leq A_2\)).
-Generally the second relation is implicit because its definition is always \(\exists R \subseteq S_1 \times S_2, P\mpar{R}\) with \(P\) a property on the relation on states, so only talking about \(R\) by defining \(P\) is sufficient.\Ludo{je comprends pas cette phrase}\Quentin{Est-ce mieux?}
+Generally the second relation is implicit because its definition is always \(\exists R \subseteq S_1 \times S_2, P\mpar{R}\) with \(P\) a property on the relation on states, so only talking about \(R\) by defining \(P\) is sufficient.\Ludo{}{je comprends pas cette phrase}\Quentin{}{Est-ce mieux?}
 However later on in this article we will define more complex relations on automata so we clarify the distinction now.
@@
 
-\Ludo{I do not understand the english + too many important properties you should give a hierarchy or at least find a better transition}\Quentin{Important properties not on the same object, this is now underlined by moving the object at the start of the sentences}
+\Ludo{}{I do not understand the english + too many important properties you should give a hierarchy or at least find a better transition}\Quentin{}{Important properties not on the same object, this is now underlined by moving the object at the start of the sentences}
 For the relation on states, the important properties we consider are being a pre-simulation and prevent the introduction of deadlocks as defined in the following.
@@
 
+In addition to the above properties, we expect from a refinement relation to prevent the introduction of deadlocks.
 Deadlocks are reachable configurations from which no further transition is possible.
 They can arise unpredictably when parallelism is involved (which is the case in our composition) and they generally break the intended behaviour of a system.
-By preventing them we could\Ludo{This seems to say that it is useless to prevent them} also\Quentin{Is it better with this additionnal word?} hope that the refinement preserves some liveness properties.
+By preventing them we \Ludo{could}{This seems to say that it is useless to prevent them} \Quentin{also}{Is it better with this additionnal word?} hope that the refinement preserves some liveness properties.
 \begin{defi}[Deadlock prevention, intuitive definition]
@@
 \end{defi}
-Actually, this requirement prevents the presence of deadlocks in the first automaton if there is a related non-deadlock configuration in the second by contraposition\Ludo{The contraposition is too tricky for me: are you sure?}\Quentin{I am, I want to say that this property is in contraposition form because the formula is not exactly what I pretend it is right there.}.
+Actually, this requirement prevents the presence of deadlocks in the first automaton if there is a related non-deadlock configuration in the second by \Ludo{contraposition}{The contraposition is too tricky for me: are you sure?}\Quentin{}{I am, I want to say that this property is in contraposition form because the formula is not exactly what I pretend it is right there.}.
 Two reasons motivated the formulation in contraposed form:
@@
 \end{itemize}
-\Quentin{Déplacé}\Ludo{je suggere un paragraphe du style}
-Unfortunately, in the general case, this property is contradictory with the other ones, this is why we restrict the general composition defined before so that we only consider a composition to be valid if it does not create deadlocks.
+Unfortunately, in the general case, this property is conflicting with the other ones because every property involving composition would be applicable on composition introducing deadlocks.
+A way to solve this conflict is to only consider a composition that do not introduce deadlocks.
 With this new condition on validity of composition we are able to define in the next sections a refinement relation where most of the properties of interest are satisfied.
-\Quentin{Il faut discuter de tout ça, je pense qu'il y a une incompréhension}
-
-\label{reply}
-``Deadlock prevention" conflicts with all the properties where composition is involved (for instance ``composition correctness") by disallowing some unwanted cases where an automaton in a hole cannot produce any action that any out-transition expects.
-In particular filling a hole with the deadlock automaton (only one state without out-transitions) is not considered a refinement for a deadlock preventing relation but any other property about composition would require it being a refinement.
-
-\Ludo{Here or before you should explain exactly WHAT YOU WANT: I do not know which are the required property which you will achieve which are incompatible, or state that you will now investigate each property and state whether it is desired / achievable/ compatible with the others: without this analysis the reader is lost}
-\Quentin{\ref{reply}}
-
-A way to solve these conflicts\Ludo{which conflict?
-can be clarified by answering the previous remark} is to characterise a composition that do not introduce deadlocks, which will be used instead of the composition introduced earlier.
+
+Before characterising a composition which does not introduce deadlocks we need to be able to tell which states are reachable because some deadlocks are not reachable and should not be taken into account as being introduced.
 \begin{defi}[Reachability]
@@
 Both automata are vending machine: Money is introduced while in state \(I\), accumulating in the money variable \(m\), when there are enough money a coffe or a tea can be ordered by taking the transitions to the states \(C\) or \(T\) and money is decreased, then the drink is served by taking the transition back to state \(I\).
+The holes added in the open version on the bottom are \(mon\) a hole which task is to verify the money inserted (coin vary depending on the country for instance) and \(serv\) which task is to serve the drink and report the exact amount served.
 
@@
 The requirements of FH-bisimulation are strictly stronger than the open automata refinement so using transitivity is sufficient.
+
+With that last property, every interesting property is proved for the presented refinement relation.
 

### 2021-06-16 2021-Refinement/report.tex
First attempt at concluding

@@
 \begin{enumerate}
-\item Formalisation of composition for open automata without requiring open pNets.
+\item The formalisation of composition for open automata without requiring open pNets.
+\item The translation of some properties of refinement relations from LTS to open automata.
 \item The characterisation of a composition that doesn't introduce deadlocks.
@@
 The interpretation of a hole is an interface with another open automaton, in which we can plug an open automaton. The plugging operation is called composition.
-In this article, composition will only refer to filling holes, other compositions like ``parallel composition" (pure interleaving) are not tackled (but one can define an open automaton that performs the parallel composition of two others).
+In this report, composition will only refer to filling holes, other compositions like ``parallel composition" (pure interleaving) are not tackled (but one can define an open automaton that performs the parallel composition of two others).
 The composition of open automata was already implicitly defined by the means of composition on pNets in previous work \cite{henrio:01299562} but never completely formalised on open automata.
@@
 Generally the second relation is implicit because its definition is always \(\exists R \subseteq S_1 \times S_2, P\mpar{R}\) with \(P\) a property on the relation on states, so only talking about \(R\) by defining \(P\) is sufficient.\Ludo{}{je comprends pas cette phrase}\Quentin{}{Est-ce mieux?}
-However later on in this article we will define more complex relations on automata so we clarify the distinction now.
+However later on in this report we will define more complex relations on automata so we clarify the distinction now.
 
@@
 \(R\) is a hole-identical simulation of \(n\) control switches by parallel composition.
-There are enough examples of proofs of refinement in this article for the reader to be able to prove it as an exercise.
+There are enough examples of proofs of refinement in this report for the reader to be able to prove it as an exercise.
 \end{exi}
@@
 \section{Conclusion}\label{sec:ccl}
-% TODO: recap contribs?
-
-The refinement presented here still do not work on the motivating example because of silent actions.
+In this report we redefined on open automata an operation from open pNets called composition.
+This operation was defined as the composition of the open pNets used to generate the open automata and not directly on open automata.
+So to reason on composition directly and to better separate the models the definition had to be given without introducing open pNets.
+Then we recalled the main properties expected from a refinement relation on a structure with composition and adapted them to open automata.
+To do that we restricted the composition so that it doesn't introduce deadlocks.
+Then we introduced several refinement relations in restricted cases to avoid dealing immediately with the hard issue of the incomparability of hole sets.
+Finally we introduced a refinement relation having all the interesting properties and dealing with the aforementioned issue at the cost of a slight modification on transitivity.
+
+However the refinement presented here still do not work on the motivating example because of silent actions.
 To be able to refine in the presence of silent action, a weak variant of the simulation is needed.

### 2021-06-16 2021-Refinement/report.tex
2 comments

--- 2021-06-15 2021-Refinement/report.tex
@@
 Open pNets are not petri nets but an intermediate representation used in the VerCors project to perform verification \cite{henrio:01252323}.
-This model is based around a hierarchical composition of generalised automata.
-Verification is the process of checking properties on a description in a specific model (for instance an automaton).
-This properties can be for instance being in some type or being deadlock free (a deadlock is an unintended state where no further action is possible).
-Open pNets with the open automaton semantics and equivalence relation introduced in previous work \cite{2007.10770} were sucessfully used to model and verify some properties of applications \cite{qin:01823507, ameurboulifa:01526055} based on BIP (Behaviour-Interaction-Priority) \cite{basu:hal-00722395} and GCM (Grid Component Model) \cite{baude:inria-00323919}.
-However equivalence relations are not always sufficient to perform verification, refinement relations are also used.
-A refinement is the verification that an implementation satisfies a specification, whereas an equivalence would check that their behaviours are the same.
-For instance a usecase on open pNet where equivalence is not sufficient can be found in an article about algorithms fo weak bisimulation on open automata \cite{wang:03126313}.
-
-The contributions of this report are:
-\begin{enumerate}
-\item Formalisation of composition for open automata without requiring open pNets.
-\item The characterisation of a composition that doesn't introduce deadlocks.
-\item The introduciton of several refinement relations for open automata that behave nicely with composition.
-\end{enumerate}
+ Verification is the process of checking that an implementation satisfies a specification.
+\Ludo{verification is more general than that (or you need to refine specification): checking typing or absence of deadlocks belong to verification}
+Open pNets with the open automaton semantics and equivalence relation introduced in previous work \cite{2007.10770} were sucessfully used to model and verify some properties of applications based on BIP  and GCM \cite{qin:01823507, ameurboulifa:01526055} \Ludo{cite and expand acronym (x2)}.
+However equivalence relations are not always sufficient to perform verification, refinement relations are also used. \Ludo{verification/refinement/equivalence needs to be refined and explained}
+For instance a usecase where open pNet where equivalence is not sufficient can be found  in an article about algorithms fo weak bisimulation on open automata \cite{wang:03126313}.
+
+\Ludo{choose: either 1) you do not refer to open pnets below and explain informally open automata here (why are they useful, what makes them different from automata), or 2) you want to refer to pnets in the following and you explain informally pnets, uatomata and the relation}
+
+The contributions of this article are \Ludo{report?} the definition of composition for open automata without having to define open pNets, and the introduction of several refinement relations for open automata.
+% TODO: expand
+
 % TODO: Related work: thesis
+
+\Ludo{RAPPEL: pour ecrire une intro: 1) on ecrit les contribs, 2) on explique avant les termeis techniques pour que le lecteur comprenne les contribs, 3) quand on a quasi fini le reste on ecrit le plan.
+ON peut commencer 1 et 2 un peu tot meme si il faut rediger le tout assez tard: on peut pas ecrire proprement un article sans avoir en tete les contribs de celui ci}
 
@@
 Families of values, or equivalently maps will be noted \(\mset{i \mapsto x_i}{i \in I}\), \(\mset{i \gets x_i}{i \in I}\) or \(x_i^{i \in I}\).
-The latter can only be used if there is a generating expression\Ludo{c est vrai pour les exemples mais pas pour les defs generiques (OA, bisim, ...): reformuler}\Quentin{Je pense que c'est aussi vrai pour les defs génériques, on définit une famille à l'aide d'une expression génératrice, par exemple \(\mpar{\beta_j}_{j \in J}\) est en réalité \(j \mapsto \beta_j\); une fonction est une expression génératrice}; for instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\).
+The latter can only be used if there is a generating expression\Ludo{c est vrai pour les exemples mais pas pour les defs generiques (OA, bisim, ...): reformuler}; for instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\).
 However \(\mbrc{\alpha \mapsto 1, \beta \mapsto 2, \gamma \mapsto 3}\) has no generating expression and is represented here with the finite version of first notation.
@@
 The action algebra \(\actions\) is another term algebra.
-It can be \Ludo{''can be'' is not much informative}\Quentin{Intended use, it is not mandatory} a subset of the terms.
+It can be \Ludo{''can be'' is not much informative} a subset of the terms.
 The formulas \(\formulas\) are at least the first order formulas over \(\terms\) and \(\actions\).
@@
 This is correct when \(\values \subseteq \rterms\) and we suppose it is the case.
-Otherwise it doesn't invalidates theorems because it can stand as a shorthand for substitution with any term which has the kept value as an interpretation\Ludo{comprends pas la fin de phrase, anglais?}\Quentin{Il manquait des mots}.
+Otherwise it doesn't invalidates theorems because it can stand as a shorthand for substitution with any term which is interpreted the kept value \Ludo{comprends pas la fin de phrase, anglais?}.
 We suppose that the interpretation of terms is compatible w.r.t.\@ substitution, that is if two terms \(t\), \(t'\) are interpreted with the same value, then replacing \(t\) by \(t'\) in a well-formed expression makes an equivalent well-formed expression.
@@
 If an undefined variable is not set before being read then its value may be any fixed value.
-When we will introduce refinements in Section \ref{sec:prelref}, setting an undefined variable will be considered a valid refinement, for instance a \(5\) bits register is a particular \(n\) bits register.
+When refining \Ludo{bizarre de parler de rafinement ici: phrase a deplacer ou introduire par: Later we will consider refinement of autoamata and ....} the automaton it can be set by the implementation, or it can be left unspecified as a parameter of the automaton (for instance a \(n\) bits register has \(n\) as parameter).
 \begin{defi}[Open transition]
@@
 
+\Ludo{here the reader needs either an intuition of the FH bisim or a definition in any case, he needs to know that he will get one or the other and when.
+For example we give below an intuitive definition of the FH bisim based on examples.}
+
+\Ludo{ If you need the notation but the def is not important you can explicitly say that the readers should refer to ??
+for the details of the def, but here I do not believe it is wise OR you could say FH bisim is useless and you do not introduce the notation but you should not use it afterwards (again not adapted I believe)}
+
 The FH-bisimulation is currently the only equivalence relation on open automata.
-The definition is not important, but the interested reader can check the article cited.
 \end{noti}
@@
 please check: you do all potential transitions with the conditions that x is the same in both.
-In any case as the matching is not linear, the simplification is not obvious}\Quentin{Same behaviour as here with the standard definition: RR-9177, sec 5.2}
+In any case as the matching is not linear, the simplification is not obvious}
 
@@
 \end{defi}
-The goal of the extractor \(\fvars{t}\) when \(t\) is a transition is to get variables that are only present in that transition.
-Also transition variables sets are disjoint from one transition to another.
-Other variables like automaton variables are already known at this point so there is no use in getting their name again.
+
+The goal of the extractor \(\fvars{t}\) when \(t\) is a transition is to get variables that are unique \Ludo{what do you mean by unique here?} to that transition.
+Other variables like automaton variables are already known at this point so there is no use in getting them \Ludo{this is not clear because I do not know what variables you ``NEED'' to ``GET'' (need and get are strange and vague to me)}.
 Also the use of this extractor benefits from this exclusion: otherwise there would always be \(\setminus V\) following it to prevent variable shadowing.
 
-\Ludo{is it really variable shadowing?}\Quentin{I don't know if the term is the same in math}
-
-\Ludo{you do not necessarily need to explain everything if this is what you need, but you miss an intuition of what this set is}\Quentin{I don't know what else I could say to give the intuition, all elements are here, in my opinion, the only thing left to build the intuition is an example}
+\Ludo{is it really variable shadowing?}
+
+\Ludo{you do not necessarily need to explain everything if this is what you need, but you miss an intuition of what this set is}
 
@@
 \begin{align*}
-	\OT{»}{»}{x}{\mbrc{l \mapsto x}}{v = L \wedge x \neq \delta}{\mbrc{}} &&
-	\OT{»}{»}{\tau}{\mbrc{l \mapsto \delta\mpar{x}, r \mapsto \act{acc}\mpar{y}}}{v = L \wedge x = y}{\mbrc{v \gets R}} &&
-	\OT{»}{»}{x}{\mbrc{r \mapsto x}}{v = R}{\mbrc{}}
-\end{align*}
-It is an alternative implementation of the enable operator which is FH-bisimilar\Ludo{makes no sense: FH bisimlar is still undefined, neither formally nor informally}\Quentin{I can remove this sentence, it adds nothing} to the previous one \cite{henrio:01299562}.
+	\OT{»}{»}{x}{\mbrc{l \mapsto x}}{v = l \wedge x \neq \delta}{\mbrc{}} &&
+	\OT{»}{»}{\tau}{\mbrc{l \mapsto \delta\mpar{x}, r \mapsto \act{acc}\mpar{y}}}{v = l \wedge x = y}{\mbrc{v \gets r}} &&
+	\OT{»}{»}{x}{\mbrc{r \mapsto x}}{v = r}{\mbrc{}}
+\end{align*}
+It is an alternative implementation of the enable operator which is \Ludo{FH-bisimilar}{makes no sense: FH bisimlar is still undefined, neither formally nor informally} to the previous one \cite{henrio:01299562}.
+Note that in this example \(r\) and \(l\) are a hole names and also closed terms: this is a naming conflict, though it is not ambiguous because \(J \cap \rterms = \emptyset\) always holds \Ludo{}{the intersection is at the same time empty and non-empty, why not use a different value (or underline them) or just say that they are in fact different names though it is easier to read using r and l for both}.
+\Ludo{le probleme ici c est qu on a l impression que tu essayes a la fois d etre tres strict et formel et pas vraiment en meme temps, il faut choisir}
 The variables that are said to be local to a transition are all the unbound variables in the expressions minus the automaton variables.
@@
 It is not local to the transition.
-When taking effective transitions, its value is not substituted with a closed term.
-For instance \nmm{\OT{»}{»}{\tau}{\mbrc{l \mapsto \tau}}{v = L \wedge \tau \neq \delta}{\mbrc{}}} is an effective transition generated from the second transition but not \nmm{\OT{»}{»}{\tau}{\mbrc{l \mapsto \tau}}{L = L \wedge \tau \neq \delta}{\mbrc{}}} (result of the forbidden substitution \(v \mapsto L\)).
-
-An run of this open automaton can be: The automaton in the hole \(l\) emits many actions, this synchronises with the only transition possible at that moment because \(v = L\).
-Then the automaton in hole \(l\) emits a \(\delta\mpar{t}\), this is synchonised with the action that sets \(v \gets R\) and the automata in hole \(r\) must emit a \(\act{acc}\mpar{t}\).
+\Ludo{In a run,}{je comprends ps cette phrase:}  when taking effective transitions (without local variables), its value is not substituted with a closed term.
+For instance \nmm{\OT{»}{»}{\tau}{\mbrc{l \mapsto \tau}}{v = l \wedge \tau \neq \delta}{\mbrc{}}} is an effective transition generated from the second transition but not \nmm{\OT{»}{»}{\tau}{\mbrc{l \mapsto \tau}}{l = l \wedge \tau \neq \delta}{\mbrc{}}} (result of the forbidden substitution \(v \mapsto l\)).
+
+An  run of this open automaton can be: The automaton in the hole \(l\) emits many actions, this synchronises with the only transition possible at that moment because \(v = l\).
+Then the automaton in hole \(l\) emits a \(\delta\mpar{t}\), this is synchonised with the action that sets \(v \gets r\) and the automata in hole \(r\) must emit a \(\act{acc}\mpar{t}\).
 Finally the automaton in the hole \(r\) emits any sequence of actions.
@@
 \end{exi}
+
 From this point open automata and open transitions are sometimes called automata and transitions for simplicity. % NEED NORMALISATION, LEFT IN CASE OF OMISSION
@@
 For example if we are interested in producing the same sequences of actions as another automaton we may want to use trace set inclusion as a refinement.
-In this section we will present the main expected properties, which are related to composition.
+Here the main expected properties are related to composition and action refinement. % LATER: explain action refinement here or remove if not tackled
 Because of composition, a relation as strong as simulation must be used.
+
+\Ludo{New}{je suggere un paragraphe du style}
+In this section we present a set of  properties that can be desirable for a refinement relation.
+We reach a point where we state a property that guarantees that the refinement does not create additional deadlock.
+Unfortunately, in the general case, this property is contradictory with the other ones, this is why we restrict the general composition defined before so that we only consider a composition  to be valid if it does not create deadlocks.
+With this new condition on validity of composition we are able to define in the next sections a refinement relation where most of the properties of interest are satisfied.
 
@@
 The first is between states of two specific automata (\(R \subseteq S_1 \times S_2\)), the second is between automata (\(A_1 \leq A_2\)).
-Generally the second relation is implicit because its definition is always \(\exists R \subseteq S_1 \times S_2, P\mpar{R}\) with \(P\) a property on the relation on states, so only talking about \(R\) by defining \(P\) is sufficient.\Ludo{je comprends pas cette phrase}\Quentin{Est-ce mieux?}
+\Ludo
+{Generally the second is implicit because its definition is always \(\exists R \subseteq S_1 \times S_2, P\mpar{R}\) with \(P\) a property, and only talking about \(R\) and \(P\) is sufficient.}{je comprends pas cette phrase}
 However later on in this article we will define more complex relations on automata so we clarify the distinction now.
-
 A relation of second kind will be called ``relation on automata" whereas a relation of the first kind is called ``relation on configurations" as defined below.
@@
 \end{defi}
-In this section we give properties on refinement relations, both on the relations on configurations and on the relation on automata.
-When relating two automata \(A_1 \mathrel{\mathcal{R}} A_2\) or their configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\), \(A_1\) will be called the implementation and \(A_2\) the specification.
-
-For the relation on automata, the important properties we consider are:
+The important properties we consider for the relation on automata are:
 \begin{defi} A relation on open automata \(\leq\) is
@@
 Reflexivity, transitivity and preorder are classical properties on relations.
-Correctness w.r.t.\@ composition means that every composition is considered a refinement.
+Correctness w.r.t.\@ composition means that every composition is considered a refinement. \Ludo{problem}{ you have not yet said that your relation was a refinement!}
 This property captures the expected behaviour of a refinement relation on a compositional structure like the open automata.
@@
 This property is useful if we want to characterise the kind of operations that can generate any refined automaton starting from the specification.
-We won't have it because extending the domain of definition of the initial valuation will be a refinement which can't be expressed with composition.
+\Ludo{}{I do not understand this: what is the domain of the valuation?}
+We won't have it because extending the domain of the initial valuation will be a refinement which can't be expressed with composition.
 Yet a ``completeness w.r.t.\@ some set of operations" is still a strong and interesting property.
@@
 
-\Ludo{I do not understand the english + too many important properties you should give a hierarchy or at least find a better transition}\Quentin{Important properties not on the same object, this is now underlined by moving the object at the start of the sentences}
-For the relation on states, the important properties we consider are being a pre-simulation and prevent the introduction of deadlocks as defined in the following.
+\Ludo{ }{I do not understand the english + too many important properties you should give a hierarchy or at least find a better transition}
+The important properties we consider for the relation on states are being a simulation and the prevention of deadlocks as defined in the following definitions.
 \begin{defi}[Pre-simulation]
@@
 Here we assume that one of the related open automata can be obtained by composing an open automaton in a hole, open automaton which can have holes itself.
-This implies that there is no relation between the related automata's holes, for instance composing \(A_i\) in \(j_i\) (\(1 \leq i \leq n\)) of \(A_0\) gives the set of holes \(J \defobject \mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}\) that is neither subset nor superset of \(J_0\).
+This implies that there is no relation between \Ludo{their}{whose?
+refine} holes, for instance composing \(A_i\) in \(j_i\) (\(1 \leq i \leq n\)) of \(A_0\) gives the set of holes \(J \defobject \mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}\) that is neither subset nor superset of \(J_0\).
 Yet we still assume that in holes with the same name, the same open automaton will be composed.
@@
 They can arise unpredictably when parallelism is involved (which is the case in our composition) and they generally break the intended behaviour of a system.
-By preventing them we could\Ludo{This seems to say that it is useless to prevent them} also\Quentin{Is it better with this additionnal word?} hope that the refinement preserves some liveness properties.
+By preventing them we \Ludo{could}{This seems to say that it is useless to prevent them} hope that the refinement preserves some liveness properties.
 \begin{defi}[Deadlock prevention, intuitive definition]
@@
 \defitem It is a pre-simulation;
-\defitem If from related states, there is a possible transition in the specification, then there is a pair of possible matching transitions from both automata:
+\defitem If from related states, there is a possible transition in the \Ludo{specification}{I do not believe specification has been defined nor implementation}, then there is \Ludo{a pair of matching transition}{A matching transition in the IMPLEMENTATION}:
 \begin{multline*}
@@
 \end{defi}
-Actually, this requirement prevents the presence of deadlocks in the first automaton if there is a related non-deadlock configuration in the second by contraposition\Ludo{The contraposition is too tricky for me: are you sure?}\Quentin{I am, I want to say that this property is in contraposition form because the formula is not exactly what I pretend it is right there.}.
-Two reasons motivated the formulation in contraposed form:
-\begin{itemize}
-\item We require a pair of matching transitions from both automata because we do not want a transition in the implementation making a configuration not a deadlock but this transition cannot be taken from the related configuration of the specification.
-\item The non contraposed formulation of the property would have required the unintuitive quantification on a possibly empty set of transition to state that they are not satisfied.
-\end{itemize}
-\Quentin{Déplacé}\Ludo{je suggere un paragraphe du style}
-Unfortunately, in the general case, this property is contradictory with the other ones, this is why we restrict the general composition defined before so that we only consider a composition to be valid if it does not create deadlocks.
-With this new condition on validity of composition we are able to define in the next sections a refinement relation where most of the properties of interest are satisfied.
-\Quentin{Il faut discuter de tout ça, je pense qu'il y a une incompréhension}
-
-\label{reply}
+Actually, this requirement prevents the presence of deadlock state in the first automaton if there is a related non-deadlock state in the second by \Ludo{contraposition}{The contraposition is too tricky for me: are you sure?}.
+Additionally, the transition preventing \Ludo{the deadlock}{in the implementation?
+how can it be the same?why is there a single one?
+this sentence makes no sense to me} has to be an existing transition in the specification.
+This is because a valid transition unmatched in the specification \Ludo{is not a deadlock}{how can a transition be a deadlock? I am completely lost}, yet \Ludo{we do not want it}{too informal}.
+The \Ludo{direct formulation}{usually you say ``the direct'' when the property seems to be defined negatively which is syntactically not the case here: you should explain or remove the remark} of the property would also have required the unintuitive quantification on a possibly empty set of transition to state that they are impossible.
+The two previous reasons motivated the formulation in contraposed form.
+
 ``Deadlock prevention" conflicts with all the properties where composition is involved (for instance ``composition correctness") by disallowing some unwanted cases where an automaton in a hole cannot produce any action that any out-transition expects.
-In particular filling a hole with the deadlock automaton (only one state without out-transitions) is not considered a refinement for a deadlock preventing relation but any other property about composition would require it being a refinement.
-
-\Ludo{Here or before you should explain exactly WHAT YOU WANT: I do not know which are the required property which you will achieve which are incompatible, or state that you will now investigate each property and state whether it is desired / achievable/ compatible with the others: without this analysis the reader is lost}
-\Quentin{\ref{reply}}
-
-A way to solve these conflicts\Ludo{which conflict?
+In particular filling a hole with the deadlock automaton (only one state without out-transitions) is not considered a refinement for a deadlock reducing relation.
+
+\Ludo{Here or before you should explain exactly WHAT YOU WANT: I do not know which are the required property which you will achieve which are incompatible, or state that you will now investigate each property and state whether it is desired / achievable/ compatible with the others: without this analysis the reader is lost}{}
+
+A way to solve \Ludo{these conflicts}{which conflict?
 can be clarified by answering the previous remark} is to characterise a composition that do not introduce deadlocks, which will be used instead of the composition introduced earlier.
@@
 
+\Ludo{a discuter}{les notations de cette formule sont vraiment pas terribles}
+
 Formally for \(\OAg \defobject A\), it gives
@@
 \end{defi}
-We can expand the alias \(V\) into \nmm{\biguplus_\subbox{1 \leq i \leq n} V_i \uplus V_0} and transform the last transition \(t\) into a pair \(\mpar{t, t_0}\) where the second transition is the one from \(A_0\) which generated \(t\).
+We can expand the alias \(V\) into \nmm{\biguplus_\subbox{1 \leq i \leq n} V_i \uplus V_0} and \Ludo{transform}{I do not understand this ``transformation''} the last transition \(t\) into a pair \(\mpar{t, t_0}\) where the second transition is the one from \(A_0\) which generated \(t\).
 Doing that makes the definition become mildly similar with the deadlock prevention one. % OR slightly
@@
 \begin{lem}
-The intuitive and working definition of deadlock prevention are equivalent.
+The \Ludo{intuitive and working definition}{add the numbers} of deadlock prevention are equivalent.
 \end{lem}
@@
 For the simultaneous composition, we may think that if the last composition of a specific composition order is non-locking, then every composition is non-locking for all composition orders.
+\Ludo{confused}{ce paragraphe est tres tres dur a lire}
 Unfortunately it is not true.
@@
 \end{exi}
-From this point and in the previous definitions, composition will only refer to non-locking composition.
+From this point \Ludo{and in the previous definitions}{confusing: This means that when we check the properties for  a refinement relation, for example correctness wrt composition,we only consider non-locking compositions.
+OU UNE AUTRE SOLUTION, MAIS COMME C EST ECRIT C EST PERURBANT}, composition will only refer to non-locking composition.
 
@@
 However it does not capture the removal of holes because other issues arise when trying to both add and remove holes.
-\begin{exi}[Example of hole-equal simulation]
-\begin{figure}
-\centering
-\input{parallel_comp.tex}
-\vrule
-\input{n_control_switch.tex}
-\caption{On the left: Parallel composition operator; On the right: n control switches automaton}
-\label{fig:hisim}
-\end{figure}
-Figure \ref{fig:hisim} introduces two related open automata with same holes \(\mbrc{l, r}\).
-The automaton on the left is a parallel composition: any hole can perform actions at any time, the actions are passed unmodified and no synchronisation is performed.
-The automaton on the right is a sequential composition with \(n\) control switches: a hole performs a sequence of actions then the other does, there are \(n\) seqences of a single automaton doing actions without the other performing some.
-
-Intuitively the right automaton is a refinement of the left automaton because the left automaton is what happens when there was no bound \(n\) in the right automaton.
-\[ R \defobject \mbrc{\mpar{l, ||} \mapsto \top, \mpar{r, ||} \mapsto \top} \]
-\(R\) is a hole-identical simulation of \(n\) control switches by parallel composition.
-There are enough examples of proofs of refinement in this article for the reader to be able to prove it as an exercise.
-\end{exi}
-\begin{exi}[Example of hole-subset simulation]
-Example of Appendix \ref{apx:composition} can be reused here.
-The automaton on Figure \ref{fig:tlf} is a refinement of the one on Figure \ref{fig:tls} by limited composition correctness (Proposition \ref{prop:cc'}).
-
-It is a simplified version of the motivation for making a refinement relation, which is the traffic light system in an article about weak-bisimulation \cite{wang:03126313}.
-It had to be modified because here the simulation is a strong-simulation (no silent actions).
-\end{exi}
-\begin{exi}[Example of hole-superset simulation]
-\begin{figure}
-\centering
-\input{Vending_machine.tex}
-\hrule
-\input{Open_vending_machine.tex}
-\caption{On the top: Vending machine; On the bottom: Open vending machine}
-\label{fig:ovm}
-\end{figure}
-Figure \ref{fig:ovm} introduces two related open automata with same states and transitions except for hole actions.
-Both automata are vending machine: Money is introduced while in state \(I\), accumulating in the money variable \(m\), when there are enough money a coffe or a tea can be ordered by taking the transitions to the states \(C\) or \(T\) and money is decreased, then the drink is served by taking the transition back to state \(I\).
-
-The automaton on the bottom is a refinement of the automaton on the top using hole-superset simulation.
-The relation on states is the same as the one for reflexivity.
-Intuitively the automaton on the bottom binds some variables to action produced by the holes, the automaton is no more free to take a transition some hole is not able to perform.
-For instace if the automaton in the hole \(mon\) can only perform \(\act{credit}\mpar{100}\) then after the composition, the automaton on the bottom should be a refinement of the one on the top.
-Actually after such a composition it is still in hole-superset simulation with the top automaton by Proposition \ref{prop:cc'}.
-\end{exi}
+
+Examples of application of the different refinement relations are given in Appendix \ref{apx:refrel}.% TODO: Maybe put them here, not in appendix
 \begin{thm} A hole-\(\triangle\) simulation is a pre-simulation. \end{thm}
@@
 However this doesn't implies \(A \leq_{\bigcup_{i \in I} J_{Bi}} C\), it has to be checked separately.
-\begin{exi}
-\begin{figure}
-\centering
-\input{identity.tex}
-\vrule
-\input{any.tex}
-\vrule
-\input{handshake_comp}
-\caption{On the left: Generic identity on holes; On the middle: Any action automaton; On the right: Handshake composition.}
-\label{fig:sevpathref}
-\end{figure}
-We have two refinement path when \(h\) is replaced by \(l\) and by \(r\) in Figure \ref{fig:sevpathref}: the parallel composition (left of Figure \ref{fig:hisim}) is a refinement of the identity on holes (right of Figure \ref{fig:sevpathref}), which is a refinement of the handshake composition (right of Figure \ref{fig:sevpathref}).
-However we do not have the parallel composition being a refinement of the handshake composition looking at \(\mbrc{l, r}\).
-
-The example also shows a property worth mentionning.
-The holes not looked at (or untracked) are equivalent to having the automaton on the middle of Figure \ref{fig:sevpathref} composed.
-Actually all the previous refinement are both ways: we can compose the Any action automaton in hole \(r\) of the parallel composition to get the other way of the refinement with the identity on holes by compositon correctness, and we transform the transition from the identity on holes into the one of the handshake composition by hole-superset refinement.
-\end{exi}
+% TODO: maybe add an example here
+
 The other interesting properties left to check are correctness w.r.t.\@ composition, context refinement, composition congruence and compatibility with FH-bisimulation.
@@
 The requirements of FH-bisimulation are strictly stronger than the open automata refinement so using transitivity is sufficient.
+
+% TODO HERE: What happens on untracked holes (untracked holes equivalent behaviour => free variables; some sort of daisy equivalence)
 
@@
 
+\section{Examples of hole-\(\triangle\) simulations}\label{apx:refrel}
+
+\subsection{Example of hole-equal simulation}
+\begin{exi}
+\begin{figure}
+\centering
+\input{parallel_comp.tex}
+\vrule
+\input{n_control_switch.tex}
+\caption{On the left: Parallel composition operator; On the right: n control switches automaton}
+\label{fig:hisim}
+\end{figure}
+Figure \ref{fig:hisim} introduces two related open automata with same holes \(\mbrc{l, r}\).
+The automaton on the left is a parallel composition: any hole can perform actions at any time, the actions are passed unmodified and no synchronisation is performed.
+The automaton on the right is a sequential composition with \(n\) control switches: a hole performs a sequence of actions then the other does, there are \(n\) seqences of a single automaton doing actions without the other performing some.
+
+Intuitively the right automaton is a refinement of the left automaton because the left automaton is what happens when there was no bound \(n\) in the right automaton.
+\[ R \defobject \mbrc{\mpar{l, ||} \mapsto \top, \mpar{r, ||} \mapsto \top} \]
+\(R\) is a hole-identical simulation of \(n\) control switches by parallel composition.
+There are enough examples of proofs of refinement in this article for the reader to be able to prove it as an exercise.
+\end{exi}
+
+\subsection{Example of hole-subset simulation}
+Example of Appendix \ref{apx:composition} can be reused here.
+The automaton on Figure \ref{fig:tlf} is a refinement of the one on Figure \ref{fig:tls} by limited composition correctness (Proposition \ref{prop:cc'}).
+
+It is a simplified version of the motivation for making a refinement relation, which is the traffic light system in an article about weak-bisimulation \cite{wang:03126313}.
+It had to be modified because here the simulation is a strong-simulation (no silent actions).
+
+\subsection{Example of hole-superset simulation}
+% TODO: vending machine of the presentation + money module
+
 \section{Proofs of properties for hole-\(\triangle\) simulation}
@@
 \item[\goal{2}:] Let \(\sigma: V \uplus V_1 \uplus \fvars{t} \to \values\).
-	We rename some variables in the domain of definition of \(\sigma\) to get \(\nu: \fvars{t_1} \to \values\).
+	We rename some variables in the input domain of \(\sigma\) to get \(\nu: \fvars{t_1} \to \values\).
 	We use \(\nu\) to prove \goal{2}, get the left side of the implication as an hypothesis and break the right side of the implication:

### 2021-06-16 2021-Refinement/report.tex

--- 2021-06-16 2021-Refinement/report.tex
@@
 In Section \ref{sec:def} we give a clean and up to date definition of open automata.
-In Section \ref{sec:comp} we define their composition without requiring the use of open pNets \Ludo{}{does this mean that previous definitions were using open pnets?
-this might be clarified in contributions but when you redo a definition you must highlight why a new definition was necessary}\Quentin{}{Yes, composition of open automata was composition of the open pNets generating them, the necessity is as stated, being independant from open pNets}.
-In Section \ref{sec:proofelts} we adapt to open automata several standard properties from refinement relations on LTS.
+In Section \ref{sec:comp} we define their composition without requiring the use of open pNets \Ludo{does this mean that previous definitions were using open pnets?
+this might be clarified in contributions but when you redo a definition you must highlight why a new definition was necessary}.
+In Section \ref{sec:proofelts} we adapt several standard properties that we use in the definition of refinement relation from LTS to open automata.
 After that Section \ref{sec:prelref} is dedicated to progressively build a refinement relation and explain the elements of this construction.
@@
 Families of values, or equivalently maps will be noted \(\mset{i \mapsto x_i}{i \in I}\), \(\mset{i \gets x_i}{i \in I}\) or \(x_i^{i \in I}\).
-The latter can only be used if there is a \Ludo{generating expression}{c'est vrai pour les exemples mais pas pour les defs generiques (OA, bisim, ...): reformuler}\Quentin{}{Je pense que c'est aussi vrai pour les defs génériques, on définit une famille à l'aide d'une expression génératrice, par exemple \(\mpar{\beta_j}_{j \in J}\) est en réalité \(j \mapsto \beta_j\); une fonction est une expression génératrice}; for instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\).
+The latter can only be used if there is a generating expression\Ludo{c est vrai pour les exemples mais pas pour les defs generiques (OA, bisim, ...): reformuler}\Quentin{Je pense que c'est aussi vrai pour les defs génériques, on définit une famille à l'aide d'une expression génératrice, par exemple \(\mpar{\beta_j}_{j \in J}\) est en réalité \(j \mapsto \beta_j\); une fonction est une expression génératrice}; for instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\).
 However \(\mbrc{\alpha \mapsto 1, \beta \mapsto 2, \gamma \mapsto 3}\) has no generating expression and is represented here with the finite version of first notation.
@@
 The action algebra \(\actions\) is another term algebra.
-It \Ludo{can be}{not much informative}\Quentin{}{Intended use, it is not mandatory} a subset of the terms.
+It can be \Ludo{''can be'' is not much informative}\Quentin{Intended use, it is not mandatory} a subset of the terms.
 The formulas \(\formulas\) are at least the first order formulas over \(\terms\) and \(\actions\).
@@
 This is correct when \(\values \subseteq \rterms\) and we suppose it is the case.
-Otherwise it doesn't invalidates theorems because it can stand as a shorthand for substitution with any term which has the kept value as an interpretation.
+Otherwise it doesn't invalidates theorems because it can stand as a shorthand for substitution with any term which has the kept value as an interpretation\Ludo{comprends pas la fin de phrase, anglais?}\Quentin{Il manquait des mots}.
 We suppose that the interpretation of terms is compatible w.r.t.\@ substitution, that is if two terms \(t\), \(t'\) are interpreted with the same value, then replacing \(t\) by \(t'\) in a well-formed expression makes an equivalent well-formed expression.
@@
 It would have avoided many effective transitions with trivially false guards like the one where \(x \mapsto 1, y \mapsto 2\), which has the guard \(1 = 2\).
-\Ludo{}{I believe that with the usual definition of the semantics of open automata it is the same ...
+\Ludo{I believe that with the usual definition of the semantics of open automata it is the same ...
 please check: you do all potential transitions with the conditions that x is the same in both.
-In any case as the matching is not linear, the simplification is not obvious}\Quentin{}{Same behaviour as here with the standard definition: RR-9177, sec 5.2}
+In any case as the matching is not linear, the simplification is not obvious}\Quentin{Same behaviour as here with the standard definition: RR-9177, sec 5.2}
 
@@
 
-\Ludo{}{is it really variable shadowing?}\Quentin{}{I don't know if the term is the same in math}
-
-\Ludo{}{you do not necessarily need to explain everything if this is what you need, but you miss an intuition of what this set is}\Quentin{}{I don't know what else I could say to give the intuition, all elements are here, in my opinion, the only thing left to build the intuition is an example}
+\Ludo{is it really variable shadowing?}\Quentin{I don't know if the term is the same in math}
+
+\Ludo{you do not necessarily need to explain everything if this is what you need, but you miss an intuition of what this set is}\Quentin{I don't know what else I could say to give the intuition, all elements are here, in my opinion, the only thing left to build the intuition is an example}
 
@@
 \end{align*}
-It is an alternative implementation of the enable operator which is \Ludo{FH-bisimilar}{makes no sense: FH bisimlar is still undefined, neither formally nor informally} to the previous one \cite{henrio:01299562}.\Quentin{}{I can remove this sentence, it adds nothing}
+It is an alternative implementation of the enable operator which is FH-bisimilar\Ludo{makes no sense: FH bisimlar is still undefined, neither formally nor informally}\Quentin{I can remove this sentence, it adds nothing} to the previous one \cite{henrio:01299562}.
 The variables that are said to be local to a transition are all the unbound variables in the expressions minus the automaton variables.
@@
 \section{Properties of a refinement relation for Open Automata}\label{sec:proofelts}
-We want to define a refinement relation on open automata, this refinement relation is expected to have some properties to be of any use.
-In this section we list and adapt to open automata the properties expected from a refinement relation.
-
-There are several kind of refinement relation depending on the properties we want.
+There are several properties we may expect from a refinement relation.
+Depending on these properties, different kinds of refinement can be used.
 For example if we are interested in producing the same sequences of actions as another automaton we may want to use trace set inclusion as a refinement.
-The main expected properties here are the standard properties on relations and the ones related to composition.
+In this section we will present the main expected properties, which are related to composition.
 Because of composition, a relation as strong as simulation must be used.
@@
 The first is between states of two specific automata (\(R \subseteq S_1 \times S_2\)), the second is between automata (\(A_1 \leq A_2\)).
-Generally the second relation is implicit because its definition is always \(\exists R \subseteq S_1 \times S_2, P\mpar{R}\) with \(P\) a property on the relation on states, so only talking about \(R\) by defining \(P\) is sufficient.\Ludo{}{je comprends pas cette phrase}\Quentin{}{Est-ce mieux?}
+Generally the second relation is implicit because its definition is always \(\exists R \subseteq S_1 \times S_2, P\mpar{R}\) with \(P\) a property on the relation on states, so only talking about \(R\) by defining \(P\) is sufficient.\Ludo{je comprends pas cette phrase}\Quentin{Est-ce mieux?}
 However later on in this article we will define more complex relations on automata so we clarify the distinction now.
@@
 
-\Ludo{}{I do not understand the english + too many important properties you should give a hierarchy or at least find a better transition}\Quentin{}{Important properties not on the same object, this is now underlined by moving the object at the start of the sentences}
+\Ludo{I do not understand the english + too many important properties you should give a hierarchy or at least find a better transition}\Quentin{Important properties not on the same object, this is now underlined by moving the object at the start of the sentences}
 For the relation on states, the important properties we consider are being a pre-simulation and prevent the introduction of deadlocks as defined in the following.
@@
 
-In addition to the above properties, we expect from a refinement relation to prevent the introduction of deadlocks.
 Deadlocks are reachable configurations from which no further transition is possible.
 They can arise unpredictably when parallelism is involved (which is the case in our composition) and they generally break the intended behaviour of a system.
-By preventing them we \Ludo{could}{This seems to say that it is useless to prevent them} \Quentin{also}{Is it better with this additionnal word?} hope that the refinement preserves some liveness properties.
+By preventing them we could\Ludo{This seems to say that it is useless to prevent them} also\Quentin{Is it better with this additionnal word?} hope that the refinement preserves some liveness properties.
 \begin{defi}[Deadlock prevention, intuitive definition]
@@
 \end{defi}
-Actually, this requirement prevents the presence of deadlocks in the first automaton if there is a related non-deadlock configuration in the second by \Ludo{contraposition}{The contraposition is too tricky for me: are you sure?}\Quentin{}{I am, I want to say that this property is in contraposition form because the formula is not exactly what I pretend it is right there.}.
+Actually, this requirement prevents the presence of deadlocks in the first automaton if there is a related non-deadlock configuration in the second by contraposition\Ludo{The contraposition is too tricky for me: are you sure?}\Quentin{I am, I want to say that this property is in contraposition form because the formula is not exactly what I pretend it is right there.}.
 Two reasons motivated the formulation in contraposed form:
@@
 \end{itemize}
-Unfortunately, in the general case, this property is conflicting with the other ones because every property involving composition would be applicable on composition introducing deadlocks.
-A way to solve this conflict is to only consider a composition that do not introduce deadlocks.
+\Quentin{Déplacé}\Ludo{je suggere un paragraphe du style}
+Unfortunately, in the general case, this property is contradictory with the other ones, this is why we restrict the general composition defined before so that we only consider a composition to be valid if it does not create deadlocks.
 With this new condition on validity of composition we are able to define in the next sections a refinement relation where most of the properties of interest are satisfied.
-
-Before characterising a composition which does not introduce deadlocks we need to be able to tell which states are reachable because some deadlocks are not reachable and should not be taken into account as being introduced.
+\Quentin{Il faut discuter de tout ça, je pense qu'il y a une incompréhension}
+
+\label{reply}
+``Deadlock prevention" conflicts with all the properties where composition is involved (for instance ``composition correctness") by disallowing some unwanted cases where an automaton in a hole cannot produce any action that any out-transition expects.
+In particular filling a hole with the deadlock automaton (only one state without out-transitions) is not considered a refinement for a deadlock preventing relation but any other property about composition would require it being a refinement.
+
+\Ludo{Here or before you should explain exactly WHAT YOU WANT: I do not know which are the required property which you will achieve which are incompatible, or state that you will now investigate each property and state whether it is desired / achievable/ compatible with the others: without this analysis the reader is lost}
+\Quentin{\ref{reply}}
+
+A way to solve these conflicts\Ludo{which conflict?
+can be clarified by answering the previous remark} is to characterise a composition that do not introduce deadlocks, which will be used instead of the composition introduced earlier.
 \begin{defi}[Reachability]
@@
 Both automata are vending machine: Money is introduced while in state \(I\), accumulating in the money variable \(m\), when there are enough money a coffe or a tea can be ordered by taking the transitions to the states \(C\) or \(T\) and money is decreased, then the drink is served by taking the transition back to state \(I\).
-The holes added in the open version on the bottom are \(mon\) a hole which task is to verify the money inserted (coin vary depending on the country for instance) and \(serv\) which task is to serve the drink and report the exact amount served.
 
@@
 The requirements of FH-bisimulation are strictly stronger than the open automata refinement so using transitivity is sufficient.
-
-With that last property, every interesting property is proved for the presented refinement relation.
 

### 2021-06-16 2021-Refinement/report.tex
2 comments

@@
 The third item of the definition has two parts:
-The first part is the main requirement, a (not proved equivalent) reordering of the pre-simulation requirement so that it better fits SMT.
+The first part is the main requirement, a (\Ludo{not proven equivalent}{risky, perhaps choose one and state that you suppose that the other is equivalent, or discuss a bit more this point + why not the same?
+symbolic reasoning is hidden here}) reordering of the pre-simulation requirement so that it better fits SMT.
 Instead of matching an effective transition to another effective transition as in the pre-simulation definition, we match an open transition to a family of covering open-transitions.
@@
 The hole-equal simulation is applicable when the related automata have the same holes.
-It is designed to capture all the refinements other than composition: Duplicating and merging states and transitions, changing variables, removing transitions, adding requirements to guards, specifying more inital variables, and many more.
+It is designed to capture all the refinements other than composition: Duplicating and merging states and transitions, changing variables, removing transitions, adding requirements to guards, specifying more initial variables, and many more.
 

### 2021-06-16 2021-Refinement/report.tex

@@
 The first is between states of two specific automata (\(R \subseteq S_1 \times S_2\)), the second is between automata (\(A_1 \leq A_2\)).
-Generally the second relation is implicit because its definition is always \(\exists R \subseteq S_1 \times S_2, P\mpar{R}\) with \(P\) a property on the relation on states, so only talking about \(R\) by defining \(P\) is sufficient.\Ludo{je comprends pas cette phrase}\Quentin{Est-ce mieux?}
-However later on in this article we will define more complex relations on automata so we clarify the distinction now.
+Generally the second relation is implicit because its definition is always \(\exists R \subseteq S_1 \times S_2, P\mpar{R}\) with \(P\) a property on the relation on states, so only talking about \(R\) by defining \(P\) is sufficient.\Ludo{}{je comprends pas cette phrase}\Quentin{}{Est-ce mieux?}
+However later on in this report we will define more complex relations on automata so we clarify the distinction now.
 
@@
 
+With that last property, every interesting property is proved for the presented refinement relation.
+
 \section{Conclusion}\label{sec:ccl}
-% TODO: recap contribs?
-
-The refinement presented here still do not work on the motivating example because of silent actions.
+In this report we redefined on open automata an operation from open pNets called composition.
+This operation was defined as the composition of the open pNets used to generate the open automata and not directly on open automata.
+So to reason on composition directly and to better separate the models the definition had to be given without introducing open pNets.
+Then we recalled the main properties expected from a refinement relation on a structure with composition and adapted them to open automata.
+To do that we restricted the composition so that it doesn't introduce deadlocks.
+Then we introduced several refinement relations in restricted cases to avoid dealing immediately with the hard issue of the incomparability of hole sets.
+Finally we introduced a refinement relation having all the interesting properties and dealing with the aforementioned issue at the cost of a slight modification on transitivity.
+
+However the refinement presented here still do not work on the motivating example because of silent actions.
 To be able to refine in the presence of silent action, a weak variant of the simulation is needed.

### 2021-06-16 2021-Refinement/report.tex
a bit of organisation in sec 6 + a few comments

--- 2021-06-16 2021-Refinement/report.tex
@@
 Example of Appendix \ref{apx:composition} can be reused here.
-The automaton on Figure \ref{fig:tlf} is a refinement of the one on Figure \ref{fig:tls} by limited composition correctness (Proposition \ref{prop:cc'}).
+The automaton on Figure \ref{fig:tlf} is a refinement of the one on Figure \ref{fig:tls} by limited composition correctness (Proposition \ref{prop:cc'} below).
 
@@
 \begin{thm} The hole-\(\triangle\) simulation on automata is a preorder. \end{thm}
+
+\paragraph{Proof sketch}
 The idea for reflexivity is that the related automata are always in the same configuration.
@@
 
+For transitivity we introduce the following.
 Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\).
@@
 \begin{prop}[Limited composition correctness]\label{prop:cc'} Hole-subset simulation is correct w.r.t.\@ composition with automata without holes. \end{prop}
+\paragraph{Proof sketch}
 For two open automata \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\) with \(J_2 = \emptyset\), let \(k \in J_1\) and \(A \defobject A_1\subst{A_2}{k}\).
@@
 \end{prop}
+\paragraph{Proof sketch}
 Let \(\reach{A_1\subst{A_3}{k}}\) be a witness that \(A_1\subst{A_3}{k}\) is non-locking.
@@
 
+\smallskip
 For composition correctness, the hole-subset simulation can only tell if there is a refinement when the composed automata have no holes.

### 2021-06-16 2021-Refinement/report.tex
Many corrections, still no TRVE conclusion

--- 2021-06-16 2021-Refinement/report.tex
@@
 The open automata model was originally designed to give the semantic of open pNets \cite{2007.10770}.
-Open pNets are not petri nets but an intermediate representation used in the VerCors project to perform verification \cite{henrio:01252323}.
-This model is based around a hierarchical composition of generalised automata.
-Verification is the process of checking properties on a description in a specific model (for instance an automaton).
-This properties can be for instance being in some type or being deadlock free (a deadlock is an unintended state where no further action is possible).
+Open pNets are not petri nets but an intermediate representation used in the VerCors project to perform verification of concurrent systems \cite{henrio:01252323}.
+Verification is the process of checking properties on a description in a specific model (for instance classical automata).
+A particular kind of verification are refinement relations.
+
+Refinement relations verifies that and implementation satisfies some properties with respect to a specification.
+The open pNets model is based around a hierarchical composition of generalised automata called pLTS.
+A properties a refinement can check on them is the non introduction of deadlocks.
+A deadlock being an unintended state where no further action is possible.
+
+The composition of open automata is inherited from open pNets as the open automaton generated from the composition on open pNets.
+This means that composition is only defined on open pNets and not directly on open automata. \Quentin{}{Clunky transition}
 Open pNets with the open automaton semantics and equivalence relation introduced in previous work \cite{2007.10770} were sucessfully used to model and verify some properties of applications \cite{qin:01823507, ameurboulifa:01526055} based on BIP (Behaviour-Interaction-Priority) \cite{basu:hal-00722395} and GCM (Grid Component Model) \cite{baude:inria-00323919}.
-However equivalence relations are not always sufficient to perform verification, refinement relations are also used.
-A refinement is the verification that an implementation satisfies a specification, whereas an equivalence would check that their behaviours are the same.
+However only an equivalence relation was used.
 For instance a usecase on open pNet where equivalence is not sufficient can be found in an article about algorithms fo weak bisimulation on open automata \cite{wang:03126313}.
@@
 \end{enumerate}
-% TODO: Related work: thesis
-
+
+This report is organised as follows:
 We begin with Section \ref{sec:notations} by giving some notations used throughout this paper.
@@
 In Section \ref{sec:def} we give a clean and up to date definition of open automata.
-In Section \ref{sec:comp} we define their composition without requiring the use of open pNets \Ludo{}{does this mean that previous definitions were using open pnets?
-this might be clarified in contributions but when you redo a definition you must highlight why a new definition was necessary}\Quentin{}{Yes, composition of open automata was composition of the open pNets generating them, the necessity is as stated, being independant from open pNets}.
+In Section \ref{sec:comp} we define their composition without requiring the use of open pNets.
 In Section \ref{sec:proofelts} we adapt to open automata several standard properties from refinement relations on LTS.
@@
 Families of values, or equivalently maps will be noted \(\mset{i \mapsto x_i}{i \in I}\), \(\mset{i \gets x_i}{i \in I}\) or \(x_i^{i \in I}\).
-The latter can only be used if there is a \Ludo{generating expression}{c'est vrai pour les exemples mais pas pour les defs generiques (OA, bisim, ...): reformuler}\Quentin{}{Je pense que c'est aussi vrai pour les defs génériques, on définit une famille à l'aide d'une expression génératrice, par exemple \(\mpar{\beta_j}_{j \in J}\) est en réalité \(j \mapsto \beta_j\); une fonction est une expression génératrice}; for instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\).
-However \(\mbrc{\alpha \mapsto 1, \beta \mapsto 2, \gamma \mapsto 3}\) has no generating expression and is represented here with the finite version of first notation.
+For instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\).
+They will be used depending on what is more convenient.
+For instance \(\mbrc{\alpha \mapsto 1, \beta \mapsto 2, \gamma \mapsto 3}\) has no simple generating expression and is better represented with the finite version of first notation.
 
@@
 There are several ways of ensuring a union is disjoint, we will indifferently either suppose sets are disjoint or rename conflicting object (useful for variables).
-The disjoint union of two maps \(\varphi: I \to X\) and \(\psi: J \to Y\) with \(I \cap J = \emptyset\) has the following signature \(\varphi \uplus \psi: I \uplus J \to X \cup Y\).
+The disjoint union of two maps \(\varphi: I \to X\) and \(\psi: J \to Y\) with \(I \cap J = \emptyset\) is noted \(\varphi \uplus \psi\) and has the following signature \(I \uplus J \to X \cup Y\).
 
@@
 The action algebra \(\actions\) is another term algebra.
-It \Ludo{can be}{not much informative}\Quentin{}{Intended use, it is not mandatory} a subset of the terms.
 The formulas \(\formulas\) are at least the first order formulas over \(\terms\) and \(\actions\).
@@
 For instance a formula with quantifiers on variables might not be provable even if it is true for all values of these variables.
-In practice the formulas will be given to a SMT solver and we cannot always make sure they have all the previous properties but, as soon as the satisfiability is consistent our theory is consistent too.
+In practice the formulas will be given to a SMT solver and we cannot always make sure they have all the previous properties but, at least any property found satsfiable by the SMT is ensured to be true.
 \(\vdash\) can hence be interpreted as an indicator of what is given to the SMT; it separates the external logic and the logic on \(\formulas\).
@@
 This is correct when \(\values \subseteq \rterms\) and we suppose it is the case.
-Otherwise it doesn't invalidates theorems because it can stand as a shorthand for substitution with any term which has the kept value as an interpretation.
+Otherwise this doesn't invalidates theorems because substitution by a value can stand as a shorthand for substitution with any term which has the value as an interpretation.
 We suppose that the interpretation of terms is compatible w.r.t.\@ substitution, that is if two terms \(t\), \(t'\) are interpreted with the same value, then replacing \(t\) by \(t'\) in a well-formed expression makes an equivalent well-formed expression.
@@
 When we will introduce refinements in Section \ref{sec:prelref}, setting an undefined variable will be considered a valid refinement, for instance a \(5\) bits register is a particular \(n\) bits register.
-\begin{defi}[Open transition]
+\begin{defi}[Open transition, Instanciated transition]
 An open transition is a tuple \nmm{\OTg} with \(s, s' \in S\) the source and target states, \(\alpha \in \actions\) the produced action, \(J' \subseteq J\) the holes involved in the transition, \(\beta_j \in \actions\) the actions of the holes, \(g \in \formulas\) the guard and \(\psi: V \to \terms\) the variable assignments.
+An open transition can have many unbound variables.
+
+An instanciated transition of the automaton is transition produced by any well-formed substitution of the unbound variables of the transition minus the automaton variables.
 \end{defi}
-An open transition can have many unbound variables.
-Actually an effective transition of the automaton is any well-formed substitution of the unbound variables of the transition minus the automaton variables.
-
 The intuition of an open automaton is a partially defined LTS with variables, guards on transitions, and parametrised actions.
@@
 Initially the automaton is in the initial state with an extension on all the variables of the initial valuation.
-In any configuration, it can perform effective transitions which source state is the current state and which guard is satisfiable in the current valuation if the holes emit the indicated actions.
-An effective transition is a transition where every variable that is not an automaton variable is instantiated with a value.
-By performing the effective transition, the automaton emits the indicated action and updates its configuration according to the target state and variable assignments.
+In any configuration, it can perform instanciated transitions which source state is the current state and which guard is satisfiable in the current valuation if the holes emit the indicated actions.
+An instanciated transition is a transition where every variable that is not an automaton variable is instantiated with a value.
+By performing the instanciated transition, the automaton emits the indicated action and updates its configuration according to the target state and variable assignments.
 
@@
 Note that the transition in the middle could have been expressed as \(\mbrc{l \mapsto \delta\mpar{x}, r \mapsto \act{acc}\mpar{x}}\).
-It would have avoided many effective transitions with trivially false guards like the one where \(x \mapsto 1, y \mapsto 2\), which has the guard \(1 = 2\).
-\Ludo{}{I believe that with the usual definition of the semantics of open automata it is the same ...
-please check: you do all potential transitions with the conditions that x is the same in both.
-In any case as the matching is not linear, the simplification is not obvious}\Quentin{}{Same behaviour as here with the standard definition: RR-9177, sec 5.2}
+It would have avoided many instanciated transitions with trivially false guards like the one where \(x \mapsto 1, y \mapsto 2\), which has the guard \(1 = 2\).
 
@@
 Let \(V\) be the variable names of the considered automaton, \(T\) its transitions and \(r\) one of its states.
-\(\fOT{r}\) are called the out-transitions of \(r\).
-\(\fIT{r}\) are called the in-transitions of \(r\).
-The local variables of a transition are all variables appearing in that transition except the global variables of the automaton.
-\begin{align*}
-	\fOT{r} & \defnotation \mset{\OTg \in T}{s = r} &
-	\fIT{r} & \defnotation \mset{\OTg \in T}{s' = r} \\
+\(\fOT[T]{r} \in T\) are called the out-transitions of the state \(r\).
+\(\fIT[T]{r} \in T\) are called the in-transitions of the state \(r\).
+When the transition set is clear from the context, it will be omitted.
+The local variables of a transition \(\fvars{t}\) are all variables appearing in transition \(t\) except the global variables of the automaton.
+\begin{align*}
+	\fOT[T]{r} & \defnotation \mset{\OTg \in T}{s = r} &
+	\fIT[T]{r} & \defnotation \mset{\OTg \in T}{s' = r} \\
 \end{align*}
@@
 Also transition variables sets are disjoint from one transition to another.
-Other variables like automaton variables are already known at this point so there is no use in getting their name again.
-Also the use of this extractor benefits from this exclusion: otherwise there would always be \(\setminus V\) following it to prevent variable shadowing.
-
-\Ludo{}{is it really variable shadowing?}\Quentin{}{I don't know if the term is the same in math}
-
-\Ludo{}{you do not necessarily need to explain everything if this is what you need, but you miss an intuition of what this set is}\Quentin{}{I don't know what else I could say to give the intuition, all elements are here, in my opinion, the only thing left to build the intuition is an example}
-
+if we need to quantify on other variables then the quantification will be done separately.
 \begin{exi}[Enable, variable-oriented]
@@
 \end{align*}
-It is an alternative implementation of the enable operator which is \Ludo{FH-bisimilar}{makes no sense: FH bisimlar is still undefined, neither formally nor informally} to the previous one \cite{henrio:01299562}.\Quentin{}{I can remove this sentence, it adds nothing}
+It is an alternative implementation of the enable operator.\footnote{It was proved FH-bisimilar to the previous one \cite{henrio:01299562}}
 The variables that are said to be local to a transition are all the unbound variables in the expressions minus the automaton variables.
@@
 It is not local to the transition.
-When taking effective transitions, its value is not substituted with a closed term.
-For instance \nmm{\OT{»}{»}{\tau}{\mbrc{l \mapsto \tau}}{v = L \wedge \tau \neq \delta}{\mbrc{}}} is an effective transition generated from the second transition but not \nmm{\OT{»}{»}{\tau}{\mbrc{l \mapsto \tau}}{L = L \wedge \tau \neq \delta}{\mbrc{}}} (result of the forbidden substitution \(v \mapsto L\)).
+When taking instanciated transitions, its value is not substituted with a closed term.
+For instance \nmm{\OT{»}{»}{\tau}{\mbrc{l \mapsto \tau}}{v = L \wedge \tau \neq \delta}{\mbrc{}}} is an instanciated transition generated from the second transition but not \nmm{\OT{»}{»}{\tau}{\mbrc{l \mapsto \tau}}{L = L \wedge \tau \neq \delta}{\mbrc{}}} (result of the forbidden substitution \(v \mapsto L\)).
 
@@
 The first is between states of two specific automata (\(R \subseteq S_1 \times S_2\)), the second is between automata (\(A_1 \leq A_2\)).
-Generally the second relation is implicit because its definition is always \(\exists R \subseteq S_1 \times S_2, P\mpar{R}\) with \(P\) a property on the relation on states, so only talking about \(R\) by defining \(P\) is sufficient.\Ludo{}{je comprends pas cette phrase}\Quentin{}{Est-ce mieux?}
+Generally the second relation is implicit because its definition is always \(\exists R \subseteq S_1 \times S_2, P\mpar{R}\) with \(P\) a property on the relation on states, so only talking about \(R\) by defining \(P\) is sufficient.
 However later on in this report we will define more complex relations on automata so we clarify the distinction now.
@@
 \end{defi}
-In this section we give properties on refinement relations, both on the relations on configurations and on the relation on automata.
 When relating two automata \(A_1 \mathrel{\mathcal{R}} A_2\) or their configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\), \(A_1\) will be called the implementation and \(A_2\) the specification.
 
-For the relation on automata, the important properties we consider are:
-\begin{defi} A relation on open automata \(\leq\) is
+In this section we first give expected properties for a refinement relation on open automata, then expected properties for a relation on configurations.
+Finally a conflict between the properties is underlined and solved.
+
+\subsection{Properties of the relation on automata}
+The important properties we consider for a refinement relation on open automata are:
+\begin{defi} A relation \(\leq\) on open automata is
 \defitem \textbf{reflexive} iff \(\forall a, a \leq a\);
@@
 
-\Ludo{}{I do not understand the english + too many important properties you should give a hierarchy or at least find a better transition}\Quentin{}{Important properties not on the same object, this is now underlined by moving the object at the start of the sentences}
-For the relation on states, the important properties we consider are being a pre-simulation and prevent the introduction of deadlocks as defined in the following.
+\subsection{Properties of the relation on states}
+The important properties we consider for the relation on configurations are being a pre-simulation and preventing the introduction of deadlocks.
+They are defined in the following.
 \begin{defi}[Pre-simulation]
@@
 In FH-bisimulation, holes with the same name will receive the same open automaton when composed, and the resulting open automaton will still be equivalent.
-Here we assume that one of the related open automata can be obtained by composing an open automaton in a hole, open automaton which can have holes itself.
+Here we will assume that one of the related open automata can be obtained by composing an open automaton in a hole, open automaton which can have holes itself.
 This implies that there is no relation between the related automata's holes, for instance composing \(A_i\) in \(j_i\) (\(1 \leq i \leq n\)) of \(A_0\) gives the set of holes \(J \defobject \mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}\) that is neither subset nor superset of \(J_0\).
@@
 However it is not sufficient to imply properties on the relation on automatons like being a preorder.
-It is only a necessary condition that we put on any relation that we call a ``simulation'' in the following.
-
-In addition to the above properties, we expect from a refinement relation to prevent the introduction of deadlocks.
+It is only a necessary condition that we put on any relation that we call a ``simulation".
+
+In addition to the above property, we expect from a refinement relation to prevent the introduction of deadlocks.
 Deadlocks are reachable configurations from which no further transition is possible.
 They can arise unpredictably when parallelism is involved (which is the case in our composition) and they generally break the intended behaviour of a system.
-By preventing them we \Ludo{could}{This seems to say that it is useless to prevent them} \Quentin{also}{Is it better with this additionnal word?} hope that the refinement preserves some liveness properties.
-\begin{defi}[Deadlock prevention, intuitive definition]
+Preventing them is also a required prerequisite for the refinement to preserve any liveness property.
+\begin{defi}[Deadlock prevention, intuitive definition]\label{def:dpid}
 A relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if:
@@
 \end{defi}
-Actually, this requirement prevents the presence of deadlocks in the first automaton if there is a related non-deadlock configuration in the second by \Ludo{contraposition}{The contraposition is too tricky for me: are you sure?}\Quentin{}{I am, I want to say that this property is in contraposition form because the formula is not exactly what I pretend it is right there.}.
-Two reasons motivated the formulation in contraposed form:
+Actually, this requirement prevents the presence of deadlocks in the first automaton if there is a related non-deadlock configuration in the second.
+The exact formulation is the contraposition of the one in the previous sentence.
+Two reasons motivated the formulation given in Definition \ref{def:dpid}:
 \begin{itemize}
 \item We require a pair of matching transitions from both automata because we do not want a transition in the implementation making a configuration not a deadlock but this transition cannot be taken from the related configuration of the specification.
-\item The non contraposed formulation of the property would have required the unintuitive quantification on a possibly empty set of transition to state that they are not satisfied.
+\item The alternative formulation of the property would have required the unintuitive quantification on a possibly empty set of transition to state that they are not satisfied.
 \end{itemize}
-Unfortunately, in the general case, this property is conflicting with the other ones because every property involving composition would be applicable on composition introducing deadlocks.
-A way to solve this conflict is to only consider a composition that do not introduce deadlocks.
+Actually the first point is not necessary, the definition can be simplified into a less intuitive version:
+\begin{defi}[Deadlock prevention, working definition]\label{def:dpwd}
+A relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if it is a pre-simulation and it satisfies the following:
+\[ \forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \]
+\end{defi}
+The requirement here is that from any related configurations, if there is a possible transition in the second automaton (whatever the value of the free variables) then there is a possible transition in the first automaton (the existential quantifier is implicit in the notation \(\vdash\)).
+The transition are not matched because the relation on configurations is a pre-simulation and it is sufficient to ensure it as will be shown in the proof.
+Apart from the matching transitions this is exactly the same explaination as the intuitive definition.
+The expected advantage of this formulation is that a SMT should behave better without the quantifiers.
+Indeed the big disjunctions are not quantifiers because in practice the out-transitions are finitary, and so is the expansion of the disjunction.
+\begin{lem}\label{lem:dred}
+The intuitive (Definition \ref{def:dpid}) and working (Definition \ref{def:dpwd}) definitions of deadlock prevention are equivalent.
+\end{lem}
+Proof of the lemma is given in Appendix \ref{apx:lemdred}.
+
+Unfortunately, in the general case, this property is conflicting with the properties about the relation on automata because every property involving composition would be applicable on composition introducing deadlocks.
+
+\subsection{Issue with deadlock prevention and composition}
+A way to solve the conflict between deadlock reduction and the properties involving composition is to only consider a composition that do not introduce deadlocks.
 With this new condition on validity of composition we are able to define in the next sections a refinement relation where most of the properties of interest are satisfied.
@@
 The exact reachability may not be representable in the formulas, hence the need of potentially over-approximating.
-
-% Another way of understanding this predicate is that it is a fixpoint of the union of valuations (function \(f\) defined below) that contains the initial valuation:
-% \begin{align*}
-	% f\mpar{p} = \mbrc{\mbox{\nmm{s' \mapsto p\mpar{s'} \vee \bigsymb{\bigvee_\subbox{\OTg \,\in\, \fIT{s'}}} p\mpar{s}\psubst{\psi} \wedge g}}} && % TODO: fix that in some way
-	% \sigma_0 \vdash \reach{A}\mpar{s_0} &&
-	% f\mpar{\reach{A}} = \reach{A}
-% \end{align*}
 \begin{defi}[Non-locking composition, intuitive definition]
@@
 The composition \(A \defobject A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is non-locking if \(A\) has a reachability predicate satisfying:
-From reachable configurations, if there was a possible transition in \(A_0\) then there is a possible transition in \(A\).
-
-\Ludo{a discuter}{les notations de cette formule sont vraiment pas terribles}
-
-Formally for \(\OAg \defobject A\), it gives
+From reachable configurations, if there was a possible transition in \(A_0\) then there is a possible transition in \(A\). Formally for \(\OAg \defobject A\), it gives
 \begin{multline*}
-	\forall s \defobject \mpar{s_0, s'} \in S_0 \times \prod_\subbox{1 \leq i \leq n} S_i, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A}\mpar{s}} \implies \\
-	\mpar{\exists t_0 \in \fOT{s_0}, \exists \nu_0: \fvars{t_0} \to \values, \sigma \uplus \nu_0 \vdash \fguard{t_0}} \implies \\
+	\forall s \defobject \mpar{s'_i}_{0 \leq i \leq n} \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A}\mpar{s}} \implies \\
+	\mpar{\exists t_0 \in \fOT{s'_0}, \exists \nu_0: \fvars{t_0} \to \values, \sigma \uplus \nu_0 \vdash \fguard{t_0}} \implies \\
 	\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t}
@@
 \end{defi}
-We can expand the alias \(V\) into \nmm{\biguplus_\subbox{1 \leq i \leq n} V_i \uplus V_0} and \Ludo{transform}{I do not understand this ``transformation''} the last transition \(t\) into a pair \(\mpar{t, t_0}\) where the second transition is the one from \(A_0\) which generated \(t\).
-Doing that makes the definition become mildly similar with the deadlock prevention one. % OR slightly
-It is not a coincidence because their goal is to caracterise the same kind of compatibility between automata.
-Actually it is possible to simplify both definition and make them even more similar.
-\begin{defi}[Deadlock prevention, working definition]
-A relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if it is a pre-simulation and it satisfies the following:
-\[ \forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \]
-\end{defi}
-The requirement here is that from any related configurations, if there is a possible transition in the second automaton (whatever the value of the free variables) then there is a possible transition in the first automaton (the existential quantifier is implicit in the notation \(\vdash\)).
-The transition are not matched because the relation on configurations is a pre-simulation and it is sufficient to ensure it as will be shown in the proof.
-Apart from the matching transitions this is exactly the same explaination as the intuitive definition.
-The expected advantage of this formulation is that a SMT should behave better without the quantifiers.
-Indeed the big disjunctions are not quantifiers because in practise the out-transitions are finitary, and so is the expansion of the disjunction. % Check if that construction is correct
-\begin{lem}
-The \Ludo{intuitive and working definition}{add the numbers} of deadlock prevention are equivalent.
-\end{lem}
+As in the previous section, the definition can be simplified into a less intuitive version:
 \begin{defi}[Non-locking composition, working definition]
@@
 \end{defi}
-\begin{lem}
+\begin{lem}\label{lem:nlced}
 The intuitive and working definition of non-locking composition are equivalent.
@@
 An illustration of both the introduction of a deadlock by composition and the definition of non-locking composition is given in Appendix \ref{apx:lockcomp}.
-Proof of both lemma are given in Appendix \ref{apx:lemeqd}.
+Proof of the lemma is given in Appendix \ref{apx:lemnlced}.
 
 This new definition of composition can replace the standard composition.
-For the simultaneous composition, we may think that if the last composition of a specific composition order is non-locking, then every composition is non-locking for all composition orders.
-\Ludo{confused}{ce paragraphe est tres tres dur a lire}
+We may think that if the simultaneous composition is non-locking, then for every composition order, each composition step is non-locking.
 Unfortunately it is not true.
-Actually even if the last composition of any order of composition is non-locking there is no guarantee that this order is non-locking at each intermediate step.
-However the opposite way is true even if uninformative:
-If there is an order of composition where every composition is non-locking then the last composition is non-locking, last composition resulting in the same automaton as the simultaneous composition.
-So the condition is better checked after the simultaneous composition or the last individual composition.
+This happens because in an intermediate composition step, a state can become a deadlock, but in a further composition step it would become unreachable.
+% However the opposite way is true: % Would need a proof, non-trivial
+% If there is an order of composition where every composition is non-locking then the last composition is non-locking, last composition resulting in the same automaton as the simultaneous composition.
+% So the condition is better checked after the simultaneous composition or the last individual composition.
 \begin{exi}
@@
 We can plug an inactive process for the network manager and the file integrity checker by composing a deadlock automaton in their holes, but always both at the same time.
-The reason for that is the simultaneous composition is non-locking, but any individual composition is locking because the state \(d1\) or \(d2\) (depending on the order) becomes a deadlock.
+The reason for that is the simultaneous composition is non-locking, but any individual composition is locking because either the state \(d1\) or \(d2\) (depending on the order) is reachable and becomes a deadlock.
 \end{exi}
-From this point \Ludo{and in the previous definitions}{confusing: This means that when we check the properties for  a refinement relation, for example correctness wrt composition,we only consider non-locking compositions.
-OU UNE AUTRE SOLUTION, MAIS COMME C EST ECRIT C EST PERURBANT}, composition will only refer to non-locking composition.
-
-A relation on open automata and its corresponding relation on configurations are simulations if the latter is a deadlock reducing pre-simulations and the former is a preorder.
-With all these properties we can now look at some concrete refinement relations.
+From this point and when checking the refinement properties, composition will only refer to non-locking composition.
 
 \section{Refinement relations in restricted cases}\label{sec:prelref}
+With all these properties explained, we can look at some concrete refinement relations.
 The main goal of this section is to explain the different aspects of refinement in restricted cases so that they are not all introduced at once in the real refinement relation.
@@
 The third item of the definition has two parts:
-The first part is the main requirement, a (\Ludo{not proven equivalent}{risky, perhaps choose one and state that you suppose that the other is equivalent, or discuss a bit more this point + why not the same?
-symbolic reasoning is hidden here}) reordering of the pre-simulation requirement so that it better fits SMT.
-Instead of matching an effective transition to another effective transition as in the pre-simulation definition, we match an open transition to a family of covering open-transitions.
+The first part is the main requirement, a stronger version of the pre-simulation requirement so that it better fits SMT.
+Instead of matching an instanciated transition to another instanciated transition as in the pre-simulation definition, we match an open transition to a family of covering open-transitions.
 The second part is directly the deadlock prevention requirement.
@@
 
+% TODO: Related work: thesis + olga
+
+% Future work
 However the refinement presented here still do not work on the motivating example because of silent actions.
@@
 
-\section{Proof of equivalent definitions}\label{apx:lemeqd}
-
-\subsection{Proof of lemma 1}
+\section{Proof of equivalent definitions}
+
+\subsection{Proof of lemma \ref{lem:dred}}\label{apx:lemdred}
 Let \(R\) be a pre-simulation between \(A_1 \defobject \OA{S_1}{s_{01}}{V_1}{\sigma_{01}}{J_1}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{V_2}{\sigma_{02}}{J_2}{T_2}\).
@@
 	However we cannot yet prove it because we don't know whether \(t_2\) and \(t_1\) match.
-	In order to get a \(t_2\) matching \(t_1\) we will use the fact that \(R\) is a pre-simulation:
+	In order to get a \(t'_2\) matching \(t_1\) we will use the fact that \(R\) is a pre-simulation:
 	\begin{multline}
@@
 
-\subsection{Proof of lemma 2}
+\subsection{Proof of lemma \ref{lem:nlced}}\label{apx:lemnlced}
 We want to prove

### 2021-06-16 2021-Refinement/report.tex
Proof sketch

@@
 An example of term algebra can be Peano integers (constant zero with arity 0, constant successor function with arity 1 and the variables), the formulas associated can use syntactic equality relation, the sum relation \(\mathit{sum}\mpar{a, b, c}: \text{``}a = b + c\text{"}\), and the product relation \(\mathit{prod}\mpar{a, b, c}: \text{``}a = b \times c\text{"}\).
-
 \begin{defi}[Unbound variables, Expressions restricted to variables, Closed expressions]
@@
 \(x = 0\), \(\forall y, \exists x, \mathit{sum}\mpar{y, z, x}\) are valid formulas, \(\forall x, \neg S\mpar{x} = 0\) is a valid closed formula, \(\fvars{x = 0} = \mbrc{x}\), \(\fvars{\forall y, \exists x, \mathit{sum}\mpar{y, z, x}} = \mbrc{z}\), \(\fvars{\forall x, \neg S\mpar{x} = 0} = \emptyset\).
-
 \begin{defi}[Values, Satisfiability, (Parallel) substitution]
@@
 By performing the instanciated transition, the automaton emits the indicated action and updates its configuration according to the target state and variable assignments.
-
 \begin{noti}[FH-bisimulation]
@@
 Initial valuations are indicated near a double lined arrow pointing to the initial state.
-
 \begin{figure}
@@
 \begin{thm} The hole-\(\triangle\) simulation on automata is a preorder. \end{thm}
-
-\paragraph{Proof sketch}
+\begin{proofsketch}
 The idea for reflexivity is that the related automata are always in the same configuration.
@@
 \(R\) is a witness of the transitivity, proof is given in Appendix \ref{apx:trans}.
+\end{proofsketch}
 \begin{prop}[Limited composition correctness]\label{prop:cc'} Hole-subset simulation is correct w.r.t.\@ composition with automata without holes. \end{prop}
-\paragraph{Proof sketch}
+\begin{proofsketch}
 For two open automata \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\) with \(J_2 = \emptyset\), let \(k \in J_1\) and \(A \defobject A_1\subst{A_2}{k}\).
@@
 \(R\) is a witness of the limited composition correctness, proof is given in Appendix \ref{apx:lchs}.
+\end{proofsketch}
 \begin{prop}[Special composition correctness]
@@
 \end{prop}
-\paragraph{Proof sketch}
+\begin{proofsketch}
 Let \(\reach{A_1\subst{A_3}{k}}\) be a witness that \(A_1\subst{A_3}{k}\) is non-locking.
@@
 \(R\) is a witness of the secial composition correctness, proof is given in Appendix \ref{apx:schs}.
-
-\smallskip
+\end{proofsketch}
 For composition correctness, the hole-subset simulation can only tell if there is a refinement when the composed automata have no holes.
@@
 \begin{thm} Open automata refinement is correct w.r.t.\@ composition \end{thm}
+\begin{proof}
 We will decompose composition into two refinement steps, transitivity will complete the proof.
@@
 By transitivity we have composition correctness.
+\end{proof}
 \begin{thm}[Context refinement] Open automata refinement is context refining. \end{thm}
+\begin{proofsketch}
 Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\).
@@
 \(\mpar{R, H}\) is a witness of \(\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{H}\), proof is given in Appendix \ref{apx:cr}.
+\end{proofsketch}
 \begin{thm}[Composition congruence] Open automata refinement is congruent for composition \end{thm}
+\begin{proofsketch}
 Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\).
@@
 \(\mpar{R, H}\) is a witness of \(\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{H}\), proof is given in Appendix \ref{apx:cong}.
+\end{proofsketch}
 \begin{thm}[FH-bisimulation compatibility] Open automata refinement is compatible with FH-bisimulation \end{thm}
-The requirements of FH-bisimulation are strictly stronger than the open automata refinement so using transitivity is sufficient.
-
+\begin{proofsketch} The requirements of FH-bisimulation are strictly stronger than the open automata refinement so using transitivity is sufficient. \end{proofsketch}
 With that last property, every interesting property is proved for the presented refinement relation.
@@
 This implementation does exactly that and forbids any extra tick.
-
 \begin{figure}
@@
 However the full traffic light will not be used in order to simplify the example, only the counter will be.
-
 \begin{figure}

### 2021-06-16 2021-Refinement/report.tex
Fixed many overfull

@@
 
-For transitivity we introduce the following.
-Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\).
-Let \(R_{12}\) be a hole-\(\triangle\) simulation of \(A_1\) by \(A_2\) and \(R_{23}\) of \(A_2\) by \(A_3\), we want to define \(R\) by saying that there exists a state \(s_2 \in S_2\) and values for \(V_2\) such that \(R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}\).
+For transitivity we need to introduce thee open automata.
+Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) be open automata.
+Let \(R_{12}\) be a hole-\(\triangle\) simulation of \(A_1\) by \(A_2\) and \(R_{23}\) of \(A_2\) by \(A_3\).
+The idea for \(R\) is that there exists a state \(s_2 \in S_2\) and values for \(V_2\) such that \(R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}\).
 However we cannot talk about states in formulas.
@@
 \begin{prop}[Special composition correctness]
-For three open automata \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3\), let \(k \in J_1 \setminus J_2\) and \(R_{12}\) be a hole-superset simulation of \(A_1\) by \(A_2\).
-There is a hole-superset simulation of \(A_1\subst{A_3}{k}\) by \(A_2\).
+If there is a hole-superset simulation of \(A_1\) by \(A_2\) and \(A_1\subst{A_3}{k}\) is non-locking, then there is a hole-superset simulation of \(A_1\subst{A_3}{k}\) by \(A_2\).
+Where \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\), \(A_3\) are open automata and \(k \in J_1 \setminus J_2\).
 \end{prop}
 \begin{proofsketch}
-Let \(\reach{A_1\subst{A_3}{k}}\) be a witness that \(A_1\subst{A_3}{k}\) is non-locking.
+Let \(R_{12}\) be a hole-superset simulation of \(A_1\) by \(A_2\) and \(\reach{A_1\subst{A_3}{k}}\) be a witness that \(A_1\subst{A_3}{k}\) is non-locking.
 The idea for the relation on configurations is to combine the non-locking composition and the already existing realtion on configurations.
@@
 \begin{proofsketch}
-Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\).
-Let \(\mpar{R_{12}, H_{12}}\) be a hole-tracking simulation of \(A_1\) by \(A_2\), \(k \in H_{12}\) and \(\reach{A_1\subst{A_3}{k}}\) be a witness that \(A_1\subst{A_3}{k}\) is non-locking.
+For three open automata \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\), let \(\mpar{R_{12}, H_{12}}\) be a hole-tracking simulation of \(A_1\) by \(A_2\), \(k \in H_{12}\) and \(\reach{A_1\subst{A_3}{k}}\) be a witness that \(A_1\subst{A_3}{k}\) is non-locking.
 The idea for the relation on configurations is that \(A_2\) simulates \(A_1\) while \(A_3\) does the same things in both compositions in the hole \(k\).
@@
 \begin{proofsketch}
-Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\).
-Let \(k \in J_1\), \(\mpar{R_{23}, H_{23}}\) be a hole-tracking simulation of \(A_2\) by \(A_3\) and \(\reach{A_1\subst{A_2}{k}}\) be a witness that \(A_1\subst{A_2}{k}\) is non-locking.
+For three open autoamta \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\), let \(k \in J_1\), \(\mpar{R_{23}, H_{23}}\) be a hole-tracking simulation of \(A_2\) by \(A_3\) and \(\reach{A_1\subst{A_2}{k}}\) be a witness that \(A_1\subst{A_2}{k}\) is non-locking.
 The idea for the relation on configurations is that \(A_3\) simulates \(A_2\) while \(A_1\) does the same things in both compositions.

### 2021-06-17 2021-Refinement/report.tex
intro de preuves pas comprises

@@
 \[ R \defobject \mpar{s_1, s_3} \mapsto \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \]
-\(R\) is a witness of the transitivity, proof is given in Appendix \ref{apx:trans}.
+\(R\) is a witness of the transitivity, proof is given in \Ludo{Appendix \ref{apx:trans}}{are we supposed to read appendix D before C.2?}.
 \end{proofsketch}
@@
 \[ R \defobject \mpar{\mpar{s_1, s_3}, s_2} \mapsto R_{12}\mpar{s_1, s_2} \wedge \reach{A_1\subst{A_3}{k}}\mpar{s_1, s_3} \]
-\(R\) is a witness of the secial composition correctness, proof is given in Appendix \ref{apx:schs}.
+\(R\) is a witness of the secial composition correctness, proof is given in Appendix \ref{apx:schs}.\Ludo{}{$y1$ et $y1'$ sortent de nulle part}
 \end{proofsketch}
@@
 
-Only one of the hole-\(\triangle\) simulations cannot tell that a non-locking composition with any automaton is a refinement because we need at the same time to add and remove holes, hence the need of the special composition correctness for hole-superset.
+\Ludo{Only one of the}{this paragraph is not clear} hole-\(\triangle\) simulations cannot tell that a non-locking composition with any automaton is a refinement because we need at the same time to add and remove holes, hence the need of the special composition correctness for hole-superset.
 Also an issue arises when trying to tell that a composition is a refinement of the base automaton: the refinement relation cannot compare the holes sets.
@@
 \section{Refinement relation for open automata}\label{sec:refinement}
-One of the solutions to keep transitivity and constraints on holes actions from same holes is to keep track of which holes are in common at each step of refinement.
+One of the \Ludo{solutions}{il manque les paragraphes qui presentent le probleme} to keep transitivity and constraints on holes actions from same holes is to keep track of which holes are in common at each step of refinement.
 The transitive refinement will have to either rename the holes without constraints or explicitly say which holes have constraints.
@@
 \end{multline*}
+\Ludo{major questions}{il me semble qu il y a pklein de trucs qu on comprend pas ici: que se passe t il si H est empty?
+on peut creer un rafinement qui fait n importe quoi avec les trous?
+on ne perd aucune propriete?
+peut etrer qu il manque juste un paragraphe qui explique l approche ses points forts et ses limitations mais l j ai pas l intuition}
 Giving \(R\) and \(H\) is sufficient to characterise the refinement, so we call \(\mpar{R, H}\) a hole-tracking simulation of \(A_1\) by \(A_2\).
@@
 
-The transitivity property becomes \(\wrel{A}{B}{X} \wedge \wrel{B}{C}{X} \implies \wrel{A}{C}{X \cap Y}\).
+The transitivity property becomes \(\wrel{A}{B}{X} \wedge \wrel{B}{C}{X} \implies \wrel{A}{C}{X \cap Y}\). \Ludo{Y}{d' ou vient le Y? peut ete qu un X est un Y?}
 It behaves the same as if the holes outside the intersection were renamed to avoid conflicts in the first place.
-This makes the comination of the transitivity proofs of hole-\(\triangle\) simulation sufficient to prove transitivity.
+This makes the combination of the transitivity proofs of hole-\(\triangle\) simulation sufficient to prove \Ludo{transitivity}{lu comme ca c est surprenant: ca semble dire que les restrictions sur les trous de la sec precedente ne sont pas vraiment utiles pour prouver la transitivite}.
 
@@
 \item[1)] \(J = J_2 \uplus J_1 \setminus \mbrc{k} = \emptyset \uplus J_1 \setminus \mbrc{k} \subseteq J_1\)
-\item[2)] We use the fact that \(R\) doesn't constrain the behaviour of \(J_2\) and initial configuration is reachable:
+\item[2)] We use the fact that \(R\) doesn't constrain the behaviour of \(J_2\) and initial configuration is \Ludo{reachable}{comment on construit la premiere disjoint union sachant que sigma 0 est l union de simga 01 et sigma 02???}:
 	\begin{align*}

### 2021-06-17 2021-Refinement/report.tex
Many small changes

@@
 
-% transitions between sections
-% TODO: CITER LES CONFERENCES
-
 \title{Refinement for open automata}
@@
 Refinement relations verifies that and implementation satisfies some properties with respect to a specification.
-The open pNets model is based around a hierarchical composition of generalised automata called pLTS.
+The open pNets model is based around a hierarchical composition of generalised automata.
 A properties a refinement can check on them is the non introduction of deadlocks.
@@
 \end{enumerate}
-
 This report is organised as follows:
-We begin with Section \ref{sec:notations} by giving some notations used throughout this paper.
+We begin with Section \ref{sec:sota} by describing the state-of-the-art.
 Then there are several sections dedicated to define all the interesting objects and properties:
+In section \ref{sec:notations} we give some notations used throughout this paper.
 In Section \ref{sec:def} we give a clean and up to date definition of open automata.
@@
 In Section \ref{sec:proofelts} we adapt to open automata several standard properties from refinement relations on LTS.
-After that Section \ref{sec:prelref} is dedicated to progressively build a refinement relation and explain the elements of this construction.
+After that Section \ref{sec:prelref} is dedicated to building refinement relations in the easy cases.
 Section \ref{sec:refinement} introduces and analyses the refinement relation on open automata.
 Finally Section \ref{sec:ccl} recapitulates the contribution and presents the work left.
+
+\section{State of the art}\label{sec:sota}
+Previous work % TODO
 
@@
 The intuition of an open automaton is a partially defined LTS with variables, guards on transitions, and parametrised actions.
-The LTS is partial in the sense that one cn plug an LTS in the hole and the surrounding LTS will react to the actions emitted by the sub-LTS put in the hole.
+The LTS is partial in the sense that one can plug an LTS in the hole and the surrounding LTS will react to the actions emitted by the sub-LTS put in the hole.
 Initially the automaton is in the initial state with an extension on all the variables of the initial valuation.
@@
 
-An run of this open automaton can be: The automaton in the hole \(l\) emits many actions, this synchronises with the only transition possible at that moment because \(v = L\).
+A run of this open automaton can be: The automaton in the hole \(l\) emits many actions, this synchronises with the only transition possible at that moment because \(v = L\).
 Then the automaton in hole \(l\) emits a \(\delta\mpar{t}\), this is synchonised with the action that sets \(v \gets R\) and the automata in hole \(r\) must emit a \(\act{acc}\mpar{t}\).
@@
 Open automata are partially specified automata, that partiality comes mostly from the holes.
-The interpretation of a hole is an interface with another open automaton, in which we can plug an open automaton. The plugging operation is called composition.
+The interpretation of a hole is an interface with another open automaton, in which we can plug an open automaton.
+The plugging operation is called composition.
 In this report, composition will only refer to filling holes, other compositions like ``parallel composition" (pure interleaving) are not tackled (but one can define an open automaton that performs the parallel composition of two others).
@@
 \begin{defi}[Composition of open automata]
-The composition of \(A_c \defobject \OAg[c]\) in the hole \(k \in J_p\) of \(A_p \defobject \OAg[p]\) is an open automaton defined as follows.
+The composition of \(A_c \defobject \OAg[c]\) in the hole \(k \in J_p\) of \(A_p \defobject \OAg[p]\) gives the open automaton defined as follows.
 \begin{align*}
@@
 Here we will assume that one of the related open automata can be obtained by composing an open automaton in a hole, open automaton which can have holes itself.
-This implies that there is no relation between the related automata's holes, for instance composing \(A_i\) in \(j_i\) (\(1 \leq i \leq n\)) of \(A_0\) gives the set of holes \(J \defobject \mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}\) that is neither subset nor superset of \(J_0\).
+This implies that there is no relation between the related automata's holes, for instance composing \(A_i\) in \(j_i\) (\(1 \leq i \leq n\)) of \(A_0\) gives the set of holes \(\mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}\) that is neither subset nor superset of \(J_0\).
 Yet we still assume that in holes with the same name, the same open automaton will be composed.
@@
 \begin{lem}\label{lem:dred}
-The intuitive (Definition \ref{def:dpid}) and working (Definition \ref{def:dpwd}) definitions of deadlock prevention are equivalent.
+The intuitive and working definitions of deadlock prevention are equivalent.
 \end{lem}
@@
 The composition \(A \defobject A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is non-locking if \(A\) has a reachability predicate satisfying:
-From reachable configurations, if there was a possible transition in \(A_0\) then there is a possible transition in \(A\). Formally for \(\OAg \defobject A\), it gives
+From reachable configurations, if there was a possible transition in \(A_0\) then there is a possible transition in \(A\).
+Formally for \(\OAg \defobject A\), it gives
 \begin{multline*}
@@
 For two open automata \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\) with \(J_2 = \emptyset\), let \(k \in J_1\) and \(A \defobject A_1\subst{A_2}{k}\).
-Let \(\reach{A}\) be a witness that \(A\) is non-locking.
+Let \(\reach{A}\) be a witness that the composition producing \(A\) is non-locking.
 The idea for the relation on configurations is that the copy of \(A_1\) in \(A\) do the same things as \(A_1\), as if we were trying to prove reflexivity.
 \[ R \defobject \mpar{\mpar{s_{1'}, s_2}, s_1} \mapsto \choice{\reach{A}\mpar{s_{1'}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1 & \text{if } s_{1'} = s_1 \\ \bot & \text{otherwise}} \]
-Where \(y_{1'}\) is the renaming of \(y_1\) from \(A_1\) in \(A\).
+Where \(y_1 \mapsto y_{1'}\) is the renaming for object of \(A_1\) in \(A\).
 \(R\) is a witness of the limited composition correctness, proof is given in Appendix \ref{apx:lchs}.
@@
 \[ R \defobject \mpar{\mpar{s_1, s_3}, s_2} \mapsto R_{12}\mpar{s_1, s_2} \wedge \reach{A_1\subst{A_3}{k}}\mpar{s_1, s_3} \]
-\(R\) is a witness of the secial composition correctness, proof is given in Appendix \ref{apx:schs}.\Ludo{}{$y1$ et $y1'$ sortent de nulle part}
+\(R\) is a witness of the special composition correctness, proof is given in Appendix \ref{apx:schs}.
 \end{proofsketch}
-For composition correctness, the hole-subset simulation can only tell if there is a refinement when the composed automata have no holes.
+The hole-subset simulation can only tell if there is a refinement when the composed automata have no holes.
 To lift this limitation we need to allow adding holes which doesn't have a direct interpretation.
+
 At first a solution using a function mapping the action performed by the new holes in the composition to the ones performed by removed hole in the base automaton was explored.
@@
 That is the reason the hole-superset simulation doesn't constrain the action performed by the added holes.
-
-\Ludo{Only one of the}{this paragraph is not clear} hole-\(\triangle\) simulations cannot tell that a non-locking composition with any automaton is a refinement because we need at the same time to add and remove holes, hence the need of the special composition correctness for hole-superset.
-Also an issue arises when trying to tell that a composition is a refinement of the base automaton: the refinement relation cannot compare the holes sets.
-This conflicts with the transitivity propriety when a hole present in both extrema of the chain is absent in an intermediate automaton.
-In that case all the constraint on holes actions are lifted even if we would like to require an equality of these actions on the transitive cloture.
+The solution adopted is to give a meaning to adding hole and only adding in a simulation.
+With the hole-superset simulation we have an interpretation to added holes:
+They are holes imposing a restriction on the transition variables.
+However with that solution we cannot remove holes so we cannot express composition corectness, hence the need of the special composition correctness for hole-superset simulation.
+
+For composition correctness, using only one of the hole-\(\triangle\) simulations cannot tell that a non-locking composition with any open automaton is a refinement of the base automaton because we need at the same time to add and remove holes.
+If we build the refinement relation as the transitive closure of all the hole-\(\triangle\) simulations then an issue arise.
+The transitivity propriety causes that when a hole present in both extrema of the chain but absent in an intermediate automaton, there is a refinement between the extrema of the chain.
+In that case all the constraint on holes actions are lifted even if we would like to require an equality of these actions on the transitive closure.
 
@@
 \end{multline*}
-\Ludo{major questions}{il me semble qu il y a pklein de trucs qu on comprend pas ici: que se passe t il si H est empty?
+\Ludo{major questions}{il me semble qu il y a plein de trucs qu on comprend pas ici: que se passe t il si H est empty?
 on peut creer un rafinement qui fait n importe quoi avec les trous?
@@
 
-The transitivity property becomes \(\wrel{A}{B}{X} \wedge \wrel{B}{C}{X} \implies \wrel{A}{C}{X \cap Y}\). \Ludo{Y}{d' ou vient le Y? peut ete qu un X est un Y?}
+The transitivity property becomes \(\wrel{A}{B}{X} \wedge \wrel{B}{C}{Y} \implies \wrel{A}{C}{X \cap Y}\).
 It behaves the same as if the holes outside the intersection were renamed to avoid conflicts in the first place.
@@
 \end{gather*}
-Where \(y_{3x}\) is the renaming of \(y_3\) from \(A_3\) in \(A_x\subst{A_3}{k}\).
+Where \(y_3 \mapsto y_{3x}\) is the renaming for object of \(A_3\) in \(A_x\subst{A_3}{k}\).
 \(\mpar{R, H}\) is a witness of \(\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{H}\), proof is given in Appendix \ref{apx:cr}.
@@
 \end{gather*}
-Where \(y_{1x}\) is the renaming of \(y_1\) from \(A_1\) in \(A_1\subst{A_x}{k}\).
+Where \(y_1 \mapsto y_{1x}\) is the renaming for object of \(A_1\) in \(A_1\subst{A_x}{k}\).
 \(\mpar{R, H}\) is a witness of \(\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{H}\), proof is given in Appendix \ref{apx:cong}.
@@
 
-% TODO: Related work: thesis + olga
-
-% Future work
 However the refinement presented here still do not work on the motivating example because of silent actions.
@@
 Let \(k \in J_1\) and \(A \defobject A_1\subst{A_2}{k}\), with \(\OAg \defobject A\).
-Let \(\reach{A}\) be a witness that \(A\) is non-locking.
+Let \(\reach{A}\) be a witness that the composition producing \(A\) is non-locking.
 \[ R \defobject \mpar{\mpar{s_{1'}, s_2}, s_1} \mapsto \choice{\reach{A}\mpar{s_{1'}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1 & \text{if } s_{1'} = s_1 \\ \bot & \text{otherwise}} \]
-Where \(y_{1'}\) is the renaming of \(y_1\) from \(A_1\) in \(A\).
+Where \(y_1 \mapsto y_{1'}\) is the renaming for object of \(A_1\) in \(A\).
 We want to prove that \(R\) is a hole-subset simulation of \(A\) by \(A_1\).
@@
 Let \(k \in J_1 \setminus J_2\) and \(A \defobject A_1\subst{A_3}{k}\), with \(\OAg \defobject A\).
-Let \(R_{12}\) be a hole-superset simulation of \(A_1\) by \(A_2\) and \(\reach{A}\) be a witness that \(A\) is non-locking.
+Let \(R_{12}\) be a hole-superset simulation of \(A_1\) by \(A_2\) and \(\reach{A}\) be a witness that the composition producing \(A\) is non-locking.
 \[ R \defobject \mpar{\mpar{s_1, s_3}, s_2} \mapsto R_{12}\mpar{s_1, s_2} \wedge \reach{A}\mpar{s_1, s_3} \]
@@
 	\item Let \(\triangle\) be \(=\).
-		We combine the proofs for two above cases and get both inclusions so \goal{0'} holds.
+		We use either one of the proof for the two above cases so \goal{0'} holds.
 	\end{itemize}
@@
 \subsection{Context refinement}\label{apx:cr}
-Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) and \(\mpar{R_{12}, H_{12}}\) be a hole-tracking simulation of \(A_1\) by \(A_2\).
-Let \(k \in H_{12}\), \(A_{13} \defobject A_1\subst{A_3}{k}\), \(A_{23} \defobject A_2\subst{A_3}{k}\) and \(\reach{A_{13}}\) be a witness that \(A_{13}\) is non-locking.
+Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) be open automata and \(\mpar{R_{12}, H_{12}}\) be a hole-tracking simulation of \(A_1\) by \(A_2\).
+Let \(k \in H_{12}\), \(A_{13} \defobject A_1\subst{A_3}{k}\), \(A_{23} \defobject A_2\subst{A_3}{k}\) and \(\reach{A_{13}}\) be a witness that the composition producing \(A_{13}\) is non-locking.
 We pose \(\OAg[13] \defobject A_{13}\) and \(\OAg[23] \defobject A_{23}\).
@@
 \end{gather*}
-Where \(y_{3x}\) is the renaming of \(y_3\) from \(A_3\) in \(A_{x3}\).
+Where \(y_3 \mapsto y_{3x}\) is the renaming for object of \(A_3\) in \(A_{x3}\).
 We want to prove that \(\mpar{R, H}\) is a witness of \(\wrel{A_{13}}{A_{23}}{H}\).
@@
 \end{gather*}
-Where \(y_{1x}\) is the renaming of \(y_1\) from \(A_1\) in \(A_{x1}\).
+Where \(y_1 \mapsto y_{1x}\) is the renaming for object of \(A_1\) in \(A_{x1}\).
 We want to prove that \(\mpar{R, H}\) is a witness of \(\wrel{A_{21}}{A_{31}}{H}\).

### 2021-06-17 2021-Refinement/report.tex
Rabea corrections

@@
 Previous work % TODO
+
+% \cite{10.1007/3-540-46428-X_19} Bellegarde2000: simulation with action refinement and silent actions working with parallel composition for LTL properties on TS; here we do not do action refinement nor silent actions but it should be done in future work, also behaviour wrt LTL properties should be checked, also our composition is more expressive than parallel compositon as parallel composition
+% \cite{10.1007/978-3-540-70881-0_26} RR5898: LTS, LTL, Deadlock reduction, non-divergence, weak-refinement, synchronised composition: Closer to what we do here, still open automata are more expressive than LTS and composition is more general than sychronised composition
+% \cite{Zhang2014} 703098: 
+% \cite{DIHEGO2020110598} :
+% \cite{DBLP:journals/corr/abs-2007-10770} weak FH:
+%  \cite{10.1145/3372884.3373161} Algorithm and str-FH:
 
@@
 
-\subsection{Properties of the relation on automata}
-The important properties we consider for a refinement relation on open automata are:
+\subsection{Properties of the relation on open automata}
+The important properties we consider for a relation on open automata are:
 \begin{defi} A relation \(\leq\) on open automata is
@@
 
-\subsection{Properties of the relation on states}
+\subsection{Properties of the relation on configurations}
 The important properties we consider for the relation on configurations are being a pre-simulation and preventing the introduction of deadlocks.
@@
 Preventing them is also a required prerequisite for the refinement to preserve any liveness property.
-\begin{defi}[Deadlock prevention, intuitive definition]\label{def:dpid}
+\begin{defi}[Deadlock reduction, intuitive definition]\label{def:dpid}
 A relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if:
@@
 Actually the first point is not necessary, the definition can be simplified into a less intuitive version:
-\begin{defi}[Deadlock prevention, working definition]\label{def:dpwd}
+\begin{defi}[Deadlock reduction, working definition]\label{def:dpwd}
 A relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if it is a pre-simulation and it satisfies the following:
@@
 \begin{lem}\label{lem:dred}
-The intuitive and working definitions of deadlock prevention are equivalent.
+The intuitive and working definitions of deadlock reduction are equivalent.
 \end{lem}
@@
 
-\subsection{Issue with deadlock prevention and composition}
+\subsection{Issue with deadlock reduction and composition}
 A way to solve the conflict between deadlock reduction and the properties involving composition is to only consider a composition that do not introduce deadlocks.
@@
 Instead of matching an instanciated transition to another instanciated transition as in the pre-simulation definition, we match an open transition to a family of covering open-transitions.
-The second part is directly the deadlock prevention requirement.
+The second part is directly the deadlock reduction requirement.
 
@@
 However we cannot talk about states in formulas.
-The solution is to expand the existential quantifier on states as we did in deadlock prevention, which is possible because states are finite.
+The solution is to expand the existential quantifier on states as we did in deadlock reduction, which is possible because states are finite.
 \[ R \defobject \mpar{s_1, s_3} \mapsto \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \]
@@
 Not renaming conflicting holes still have an interest.
-If we are trying to build an automaton \(A\) with several constraints \(\wrel{A}{B_i}{J_{Bi}}, i \in I\) -method B like- and each \(B_i\) is a refinement of some automaton \(C\) then we can have each \(B_i\) constrain a different subset of \(A\)'s holes.
-On each individual path \(A \leq_{J_{Bi}} B_i \leq_{J_{Bi}} C\), some holes of \(A\) are unconstrained but when considering all path they are all constrained.
-However this doesn't implies \(A \leq_{\bigcup_{i \in I} J_{Bi}} C\), it has to be checked separately.
+If we are trying to build an automaton \(A\) with several constraints \(\wrel{A}{A_i}{J_{Ai}}, i \in I\) (as done in B method \cite{cansell:inria-00099794}) and each \(A_i\) is a refinement of some automaton \(C\) then we can have each \(A_i\) constrain a different subset of \(A\)'s holes.
+On each individual path \(A \leq_{J_{Ai}} A_i \leq_{J_{Ai}} C\), some holes of \(A\) are unconstrained but when considering all path they are all constrained.
+However this doesn't implies \(A \leq_{\bigcup_{i \in I} J_{Ai}} C\), it has to be checked separately.
 \begin{exi}
@@
 \input{handshake_comp}
-\caption{On the left: Generic identity on holes; On the middle: Any action automaton; On the right: Handshake composition.}
+\caption{On the left: Generic identity on holes; On the center: Any action automaton; On the right: Handshake composition.}
 \label{fig:sevpathref}
 \end{figure}
-We have two refinement path when \(h\) is replaced by \(l\) and by \(r\) in Figure \ref{fig:sevpathref}: the parallel composition (left of Figure \ref{fig:hisim}) is a refinement of the identity on holes (right of Figure \ref{fig:sevpathref}), which is a refinement of the handshake composition (right of Figure \ref{fig:sevpathref}).
+We have two refinement paths when \(h\) is replaced by \(l\) and by \(r\) in identity on holes (left of Figure \ref{fig:sevpathref}): the parallel composition (left of Figure \ref{fig:hisim}) is a refinement of the identity on holes, which is a refinement of the handshake composition (right of Figure \ref{fig:sevpathref}).
 However we do not have the parallel composition being a refinement of the handshake composition looking at \(\mbrc{l, r}\).
@@
 The example also shows a property worth mentionning.
-The holes not looked at (or untracked) are equivalent to having the automaton on the middle of Figure \ref{fig:sevpathref} composed.
-Actually all the previous refinement are both ways: we can compose the Any action automaton in hole \(r\) of the parallel composition to get the other way of the refinement with the identity on holes by compositon correctness, and we transform the transition from the identity on holes into the one of the handshake composition by hole-superset refinement.
+The holes not looked at (or untracked) are equivalent to having the any action automaton (center of Figure \ref{fig:sevpathref}) composed.
+Actually all the previous refinement are both ways: we can compose the any action automaton in hole \(r\) of the parallel composition to get the other way of the refinement with the identity on holes by compositon correctness, and we transform the transition from the identity on holes into the one of the handshake composition by hole-superset refinement.
 \end{exi}
@@
 Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(k \in J_1\) such that \(A_1\subst{A_2}{k}\) is non-locking.
-We pose
-\begin{gather*}
-	A'_2 \defobject \OA{S_2}{s_{02}}{V_2}{\sigma_{02}}{\emptyset}{T'_2} \\
-	T'_2 \defobject \mset{\OT{s}{s'}{\alpha}{\mbrc{}}{g}{\psi}}{\OTg \in T_2}
-\end{gather*}
+We pose \(A'_2\) as \(A_2\) stripped of its holes.
+\begin{align*}
+	A'_2 \defobject & \OA{S_2}{s_{02}}{V_2}{\sigma_{02}}{\emptyset}{T'_2} \\
+	T'_2 \defobject & \mset{\OT{s}{s'}{\alpha}{\mbrc{}}{g}{\psi}}{\OTg \in T_2}
+\end{align*}
 By limited composition correctness we have \(\wrel{A_1\subst{A'_2}{k}}{A_1}{J_1 \setminus \mbrc{k}}\).
@@
 The idea for the relation on configurations is that \(A_2\) simulates \(A_1\) while \(A_3\) does the same things in both compositions in the hole \(k\).
-\begin{gather*}
-	R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_1\subst{A_3}{k}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \\
-	H \defobject J_3 \uplus H_{12} \setminus \mbrc{k}
-\end{gather*}
+\begin{align*}
+	R \defobject & \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_1\subst{A_3}{k}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \\
+	H \defobject & J_3 \uplus H_{12} \setminus \mbrc{k}
+\end{align*}
 Where \(y_3 \mapsto y_{3x}\) is the renaming for object of \(A_3\) in \(A_x\subst{A_3}{k}\).
@@
 \begin{proofsketch}
-For three open autoamta \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\), let \(k \in J_1\), \(\mpar{R_{23}, H_{23}}\) be a hole-tracking simulation of \(A_2\) by \(A_3\) and \(\reach{A_1\subst{A_2}{k}}\) be a witness that \(A_1\subst{A_2}{k}\) is non-locking.
+For three open automata \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\), let \(k \in J_1\), \(\mpar{R_{23}, H_{23}}\) be a hole-tracking simulation of \(A_2\) by \(A_3\) and \(\reach{A_1\subst{A_2}{k}}\) be a witness that \(A_1\subst{A_2}{k}\) is non-locking.
 The idea for the relation on configurations is that \(A_3\) simulates \(A_2\) while \(A_1\) does the same things in both compositions.
-\begin{gather*}
-	R \defobject \mpar{\mpar{s_{12}, s_2}, \mpar{s_{13}, s_3}} \mapsto \choice{R_{23}\mpar{s_2, s_3} \wedge \reach{A_1\subst{A_2}{k}}\mpar{s_{12}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{12} = v_{13} & \text{if } s_{12} = s_{13} \\ \bot & \text{otherwise}} \\
-	H \defobject H_{23} \uplus J_1 \setminus \mbrc{k}
-\end{gather*}
+\begin{align*}
+	R \defobject & \mpar{\mpar{s_{12}, s_2}, \mpar{s_{13}, s_3}} \mapsto \choice{R_{23}\mpar{s_2, s_3} \wedge \reach{A_1\subst{A_2}{k}}\mpar{s_{12}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{12} = v_{13} & \text{if } s_{12} = s_{13} \\ \bot & \text{otherwise}} \\
+	H \defobject & H_{23} \uplus J_1 \setminus \mbrc{k}
+\end{align*}
 Where \(y_1 \mapsto y_{1x}\) is the renaming for object of \(A_1\) in \(A_1\subst{A_x}{k}\).
@@
 \end{figure}
-The clock on the left side of Figure \ref{fig:anytick} transmit the actions of its hole unchanged until the clock imposes a \(\act{tick}\) on its hole.
+The clock on the left side of Figure \ref{fig:anytick} transmits the actions of its hole unchanged until the clock imposes a \(\act{tick}\) on its hole.
 This can model a physical clock, because physical time ticks cannot be delayed.
@@
 There are two deadlocks:
-The first is in the state \(1S\), which correspond to the clock trying to imppose a tick when the counter is not set.
-The second is in the state \(1C\), which correspond to the clock trying to impose a tick when the counter has reached the amount peviously set, but not has not yet reported it to the environment.
+The first is in the state \(1S\), which corresponds to the clock trying to imppose a tick when the counter is not set.
+The second is in the state \(1C\), which corresponds to the clock trying to impose a tick when the counter has reached the amount previously set, but not has not yet reported it to the environment.
 These deadlocks could have been in the specification in which case they were intended, but it is not the case here.
@@
 We could have defined the non-locking composition so that this is considered as an intended deadlock, making the requirement symmetric.
-However the the semantics of composition in a hole is asymmetric and the considered specification -as in the deadlock prevention- is the parent automaton.
+However the the semantics of composition in a hole is asymmetric and the considered specification -as in the deadlock reduction- is the parent automaton.
 \end{exi}
@@
 
-\subsection{Proof of lemma \ref{lem:dred}}\label{apx:lemdred}
+\subsection{Proof of Lemma \ref{lem:dred}}\label{apx:lemdred}
 Let \(R\) be a pre-simulation between \(A_1 \defobject \OA{S_1}{s_{01}}{V_1}{\sigma_{01}}{J_1}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{V_2}{\sigma_{02}}{J_2}{T_2}\).
@@
 
-\subsection{Proof of lemma \ref{lem:nlced}}\label{apx:lemnlced}
+\subsection{Proof of Lemma \ref{lem:nlced}}\label{apx:lemnlced}
 We want to prove
@@
 	\[ \sigma \uplus \nu \uplus \mu \vdash \fguard{t} \hyp{3'} \]
-	At this point we have a \(t\) which is composed of a transition in \(A_p\) and one in \(A_c\) so unlike lemma 1 we do not need to check that two transitions matches.
+	At this point we have a \(t\) which is composed of a transition in \(A_p\) and one in \(A_c\) so unlike Lemma \ref{lem:dred} we do not need to check that two transitions matches.
 	The current goal is:
@@
 Let \(R\) be a relation on configurations.
-The condition \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\) is in both definitions and the deadlock prevention requirement will not be used so proving the following is sufficient:
+The condition \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\) is in both definitions and the deadlock reduction requirement will not be used so proving the following is sufficient:
 \begin{multline}
@@
 	\goal{2b} also holds because \(J'_1 \cap J = J'_1 \setminus \mbrc{k} = J'\), composition doesn't change the actions of the holes involved and the valuation coincide on the renamed variables.
-	\goal{2c} is proved using \hyp{1c} (\(g \equiv g_1\) or \(g \equiv g_1 \wedge \dots\)).
+	\goal{2c} is proved using \hyp{1c} (\(g \iff g_1\) or \(g \iff g_1 \wedge \dots\)).
 	For \goal{2d} we use \hyp{1a} with the preservation of reachability across transitions, \hyp{1b} and the fact that the valuations coincide on the renamed values:
@@
 We pose \(\OAg[13] \defobject A_{13}\) and \(\OAg[23] \defobject A_{23}\).
-\begin{gather*}
-	R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \\
-	H \defobject J_3 \uplus H_{12} \setminus \mbrc{k}
-\end{gather*}
+\begin{align*}
+	R \defobject & \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \\
+	H \defobject & J_3 \uplus H_{12} \setminus \mbrc{k}
+\end{align*}
 Where \(y_3 \mapsto y_{3x}\) is the renaming for object of \(A_3\) in \(A_{x3}\).
@@
 	\goal{3b} holds because the valuations for the actions of the holes in \(J_3\) coincide by definition of \(\nu'\) and by \hyp{3b} for the others.
-	For \goal{3c} we have two cases, if \(k \notin J'_1\) then \(g_{23x} \equiv g_{2x}\) and \hyp{3c} is sufficient, if \(k \in J'_1\) then \(g_{23x} \equiv g_{2x} \wedge g_3 \wedge \alpha_3 = \beta_{2xk}\) so we also need \hyp{2d} (\(g_{13} \equiv g_1 \wedge g_3 \wedge \alpha_3 = \beta_{1k}\)) and \hyp{3b} for the value \(k\) (\(\beta_{1k} = \beta_{2xk}\)).
+	For \goal{3c} we have two cases, if \(k \notin J'_1\) then \(g_{23x} \iff g_{2x}\) and \hyp{3c} is sufficient, if \(k \in J'_1\) then \(g_{23x} \iff g_{2x} \wedge g_3 \wedge \alpha_3 = \beta_{2xk}\) so we also need \hyp{2d} (\(g_{13} \iff g_1 \wedge g_3 \wedge \alpha_3 = \beta_{1k}\)) and \hyp{3b} for the value \(k\) (\(\beta_{1k} = \beta_{2xk}\)).
 	\goal{3d} is proved using \hyp{3d}, \hyp{2b} with the preservation of reachability across transitions (+ \hyp{2d}), \hyp{2c} and the fact that \(A_3\) performs the same transition with same values in both composed automata:
@@
 We pose \(\OAg[21] \defobject A_{21}\) and \(\OAg[31] \defobject A_{31}\).
-\begin{gather*}
-	R \defobject \mpar{\mpar{s_{12}, s_2}, \mpar{s_{13}, s_3}} \mapsto \choice{R_{23}\mpar{s_2, s_3} \wedge \reach{A_{21}}\mpar{s_{12}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{12} = v_{13} & \text{if } s_{12} = s_{13} \\ \bot & \text{otherwise}} \\
-	H \defobject H_{23} \uplus J_1 \setminus \mbrc{k}
-\end{gather*}
+\begin{align*}
+	R \defobject & \mpar{\mpar{s_{12}, s_2}, \mpar{s_{13}, s_3}} \mapsto \choice{R_{23}\mpar{s_2, s_3} \wedge \reach{A_{21}}\mpar{s_{12}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{12} = v_{13} & \text{if } s_{12} = s_{13} \\ \bot & \text{otherwise}} \\
+	H \defobject & H_{23} \uplus J_1 \setminus \mbrc{k}
+\end{align*}
 Where \(y_1 \mapsto y_{1x}\) is the renaming for object of \(A_1\) in \(A_{x1}\).
@@
 	\goal{3b} holds because the valuations for the actions of the holes in \(J_1\) coincide by definition of \(\nu'\) and by \hyp{3b} for the others (\(k \notin H\)).
-	For \goal{3c} we have two cases, if \(k \notin J'_{12}\) then \(g_{31x} \equiv g_{13}\) and \hyp{2d} is sufficient (\(g_{21} \equiv g_{13}\)), if \(k \in J'_{13}\) then \(g_{31x} \equiv g_{13} \wedge g_{3x} \wedge \alpha_{3x} = \beta_{13k}\) so we also need \hyp{3c} and \hyp{3a} in addition to \hyp{2d} (\(g_{21} \equiv g_{13} \wedge \alpha_2 = \beta_{12k}\)).
+	For \goal{3c} we have two cases, if \(k \notin J'_{12}\) then \(g_{31x} \iff g_{13}\) and \hyp{2d} is sufficient (\(g_{21} \iff g_{13}\)), if \(k \in J'_{13}\) then \(g_{31x} \iff g_{13} \wedge g_{3x} \wedge \alpha_{3x} = \beta_{13k}\) so we also need \hyp{3c} and \hyp{3a} in addition to \hyp{2d} (\(g_{21} \iff g_{13} \wedge \alpha_2 = \beta_{12k}\)).
 	\goal{3d} is proved using \hyp{3d}, \hyp{2b} with the preservation of reachability across transitions (+ \hyp{2d}), \hyp{2c} and the fact that \(A_1\) performs the same transition with same values in both composed automata:

### 2021-06-17 2021-Refinement/report.tex
correction typos

@@
 
-Notations are parameterised by a term algebra \(\terms\).
+Notations are parametrized by a term algebra \(\terms\).
 As any term algebra it has constant symbols with arity, variables, and a typing mechanism to distinguish well-formed and ill-formed terms.
@@
 For instance a formula with quantifiers on variables might not be provable even if it is true for all values of these variables.
-In practice the formulas will be given to a SMT solver and we cannot always make sure they have all the previous properties but, at least any property found satsfiable by the SMT is ensured to be true.
+In practice the formulas will be given to a SMT solver and we cannot always make sure they have all the previous properties but, at least any property found satisfiable by the SMT is ensured to be true.
 \(\vdash\) can hence be interpreted as an indicator of what is given to the SMT; it separates the external logic and the logic on \(\formulas\).
@@
 \begin{defi}[Open automaton]
-A open automaton is a tuple \(\OAg\) with \(S\) the set of states, \(s_0 \in S\) the initial state, \(V\) the set of variable names unique to this automaton, \(\sigma_0: V' \to \values\) the initial valuation of variables where \(V' \subseteq V\), \(J\) the set of hole names and \(T\) the set of open transitions.
+An open automaton is a tuple \(\OAg\) with \(S\) the set of states, \(s_0 \in S\) the initial state, \(V\) the set of variable names unique to this automaton, \(\sigma_0: V' \to \values\) the initial valuation of variables where \(V' \subseteq V\), \(J\) the set of hole names and \(T\) the set of open transitions.
 A pair of a state and a valuation is called a configuration.
@@
 States names are indicated inside the circles and transitions labels are drawn near their corresponding arrow.
-The open transitions do not indicate the source and target states since that is the role of the transitions arrows; only the emmited action is on the bottom side of open transitions.
+The open transitions do not indicate the source and target states since that is the role of the transitions arrows; only the emitted action is on the bottom side of open transitions.
 Initial valuations are indicated near a double lined arrow pointing to the initial state.
@@
 \end{exi}
-Finally we can define some utilitary functions:
+Finally we can define some useful functions:
 \begin{defi}[Guard, Out-transition, Transition variables]
@@
 A run of this open automaton can be: The automaton in the hole \(l\) emits many actions, this synchronises with the only transition possible at that moment because \(v = L\).
-Then the automaton in hole \(l\) emits a \(\delta\mpar{t}\), this is synchonised with the action that sets \(v \gets R\) and the automata in hole \(r\) must emit a \(\act{acc}\mpar{t}\).
+Then the automaton in hole \(l\) emits a \(\delta\mpar{t}\), this is synchronised with the action that sets \(v \gets R\) and the automata in hole \(r\) must emit a \(\act{acc}\mpar{t}\).
 Finally the automaton in the hole \(r\) emits any sequence of actions.
@@
 \end{defi}
-The action emitted when \(A_c\) makes a transition is sychronised with the action of the hole \(k\) in transitions of \(A_p\) which have it as a hole action (first transition set, \(\alpha_c = \beta_k\)).
+The action emitted when \(A_c\) makes a transition is synchronised with the action of the hole \(k\) in transitions of \(A_p\) which have it as a hole action (first transition set, \(\alpha_c = \beta_k\)).
 The composition may look like a handshake, with both automata running in parallel (product of states and joint variables) however it is asymmetric because it is the first automaton that decides when the second can evolve, while the first automaton can evolve independently as soon as the hole is not involved in the open transition considered.
@@
 Hence only the holes in common have to match their actions.
-However it is not sufficient to imply properties on the relation on automatons like being a preorder.
+However it is not sufficient to imply properties on the relation on automata like being a preorder.
 It is only a necessary condition that we put on any relation that we call a ``simulation".
@@
 The transition are not matched because the relation on configurations is a pre-simulation and it is sufficient to ensure it as will be shown in the proof.
-Apart from the matching transitions this is exactly the same explaination as the intuitive definition.
+Apart from the matching transitions this is exactly the same explanation as the intuitive definition.
 The expected advantage of this formulation is that a SMT should behave better without the quantifiers.
@@
 In that state we want to synchronise the files before working, or work on the local version as a fallback.
-If the preferred version is the remote one, we go in state \(d1\) asking the netwotk manager to fetch the lastest version, then ask the integrity checker to validate the files.
+If the preferred version is the remote one, we go in state \(d1\) asking the network manager to fetch the latest version, then ask the integrity checker to validate the files.
 If the preferred version is the local one, we go in state \(d2\) asking for the integrity checker to validate the local files, then ask the network manager to push them.
@@
 The automaton on the left is a parallel composition: any hole can perform actions at any time, the actions are passed unmodified and no synchronisation is performed.
-The automaton on the right is a sequential composition with \(n\) control switches: a hole performs a sequence of actions then the other does, there are \(n\) seqences of a single automaton doing actions without the other performing some.
-
-Intuitively the right automaton is a refinement of the left automaton because the left automaton is what happens when there was no bound \(n\) in the right automaton.
+The automaton on the right is a sequential composition with \(n\) control switches: a hole performs a sequence of actions then the other does, there are \(n\) sequences of a single automaton doing actions without the other performing some.
+
+Intuitively the right automaton is a refinement of the left automaton because the left automaton is what happen when there was no bound \(n\) in the right automaton.
 \[ R \defobject \mbrc{\mpar{l, ||} \mapsto \top, \mpar{r, ||} \mapsto \top} \]
@@
 Figure \ref{fig:ovm} introduces two related open automata with same states and transitions except for hole actions.
-Both automata are vending machine: Money is introduced while in state \(I\), accumulating in the money variable \(m\), when there are enough money a coffe or a tea can be ordered by taking the transitions to the states \(C\) or \(T\) and money is decreased, then the drink is served by taking the transition back to state \(I\).
+Both automata are vending machine: Money is introduced while in state \(I\), accumulating in the money variable \(m\), when there are enough money a coffee or a tea can be ordered by taking the transitions to the states \(C\) or \(T\) and money is decreased, then the drink is served by taking the transition back to state \(I\).
 The holes added in the open version on the bottom are \(mon\) a hole which task is to verify the money inserted (coin vary depending on the country for instance) and \(serv\) which task is to serve the drink and report the exact amount served.
@@
 Intuitively the automaton on the bottom binds some variables to action produced by the holes, the automaton is no more free to take a transition some hole is not able to perform.
-For instace if the automaton in the hole \(mon\) can only perform \(\act{credit}\mpar{100}\) then after the composition, the automaton on the bottom should be a refinement of the one on the top.
+For instance if the automaton in the hole \(mon\) can only perform \(\act{credit}\mpar{100}\) then after the composition, the automaton on the bottom should be a refinement of the one on the top.
 Actually after such a composition it is still in hole-superset simulation with the top automaton by Proposition \ref{prop:cc'}.
@@
 Let \(R_{12}\) be a hole-superset simulation of \(A_1\) by \(A_2\) and \(\reach{A_1\subst{A_3}{k}}\) be a witness that \(A_1\subst{A_3}{k}\) is non-locking.
-The idea for the relation on configurations is to combine the non-locking composition and the already existing realtion on configurations.
+The idea for the relation on configurations is to combine the non-locking composition and the already existing relation on configurations.
 \[ R \defobject \mpar{\mpar{s_1, s_3}, s_2} \mapsto R_{12}\mpar{s_1, s_2} \wedge \reach{A_1\subst{A_3}{k}}\mpar{s_1, s_3} \]
@@
 At first a solution using a function mapping the action performed by the new holes in the composition to the ones performed by removed hole in the base automaton was explored.
-It was abandonned because the base automaton has nothing intelligent to tell about the action required by the composed automata.
+It was abandoned because the base automaton has nothing intelligent to tell about the action required by the composed automata.
 That is the reason the hole-superset simulation doesn't constrain the action performed by the added holes.
@@
 They are holes imposing a restriction on the transition variables.
-However with that solution we cannot remove holes so we cannot express composition corectness, hence the need of the special composition correctness for hole-superset simulation.
+However with that solution we cannot remove holes so we cannot express composition correctness, hence the need of the special composition correctness for hole-superset simulation.
 
@@
 
-The example also shows a property worth mentionning.
+The example also shows a property worth mentioning.
 The holes not looked at (or untracked) are equivalent to having the any action automaton (center of Figure \ref{fig:sevpathref}) composed.
-Actually all the previous refinement are both ways: we can compose the any action automaton in hole \(r\) of the parallel composition to get the other way of the refinement with the identity on holes by compositon correctness, and we transform the transition from the identity on holes into the one of the handshake composition by hole-superset refinement.
+Actually all the previous refinement are both ways: we can compose the any action automaton in hole \(r\) of the parallel composition to get the other way of the refinement with the identity on holes by composition correctness, and we transform the transition from the identity on holes into the one of the handshake composition by hole-superset refinement.
 \end{exi}
@@
 This example reuses the counter introduced in Figure \ref{fig:tlh}.
-The behaviour of the counter is to count external \(\act{tick}\) actions up to the amount set by action \(\act{set}\mpar{x}\) then to notify the environnement that this amount of time elapsed.
-In the traffic light example the clock is not specified, we will introduce deadlocks using a wisely choosen clock specification.
+The behaviour of the counter is to count external \(\act{tick}\) actions up to the amount set by action \(\act{set}\mpar{x}\) then to notify the environment that this amount of time elapsed.
+In the traffic light example the clock is not specified, we will introduce deadlocks using a wisely chosen clock specification.
 However the full traffic light will not be used in order to simplify the example, only the counter will be.
@@
 There are two deadlocks:
-The first is in the state \(1S\), which corresponds to the clock trying to imppose a tick when the counter is not set.
+The first is in the state \(1S\), which corresponds to the clock trying to impose a tick when the counter is not set.
 The second is in the state \(1C\), which corresponds to the clock trying to impose a tick when the counter has reached the amount previously set, but not has not yet reported it to the environment.
@@
 
-We should successfully caracterise the second composition as non-locking but fail for the first.
+We should successfully characterise the second composition as non-locking but fail for the first.
 \begin{itemize}
@@
 \item[\goal{0'}:] \(t\) is a transition built from \(t_1\) so it has its holes.
-	Additionnally either \(k \notin J'_1\) so \(J' = J'_1\) or \(k \in J'_1\) so \(J' = \emptyset \uplus J'_1 \setminus \mbrc{k}\) because \(A_2\) has no holes.
+	Additionally either \(k \notin J'_1\) so \(J' = J'_1\) or \(k \in J'_1\) so \(J' = \emptyset \uplus J'_1 \setminus \mbrc{k}\) because \(A_2\) has no holes.
 	Either case \(J'_1 \cap J = J'_1 \setminus \mbrc{k} = \mpar{J'_1 \setminus \mbrc{k}} \cap J_1 = J' \cap J_1\).
@@
 \item[\goal{1}:] Let \nmm{\sigma: V \uplus V_1 \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
-	We use dummy values for the variables in \nmm{\biguplus_\subbox{t \in \fOT{s}} \fvars{t}} to get the left side of the implication (independant from these values), immediately broken into
+	We use dummy values for the variables in \nmm{\biguplus_\subbox{t \in \fOT{s}} \fvars{t}} to get the left side of the implication (independent from these values), immediately broken into
 	\begin{gather}
@@
 \item[\goal{2}:] Let \nmm{\sigma: V \uplus V_2 \uplus \fvars{t} \to \values}.
-	We use dummy values for the variables in \nmm{\biguplus_\subbox{t_{2x} \in \fOT{s_2}} \fvars{t_{2x}}} to get the left side of the implication (independant from these values), immediately broken into
+	We use dummy values for the variables in \nmm{\biguplus_\subbox{t_{2x} \in \fOT{s_2}} \fvars{t_{2x}}} to get the left side of the implication (independent from these values), immediately broken into
 	\begin{gather}
@@
 	Let \nmm{\sigma: V \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values}.
-	We use dummy values for the variables in \nmm{\biguplus_\subbox{t \in \fOT{s}} \fvars{t}} to get the left side of the implication (independant from these values), immediately broken into
+	We use dummy values for the variables in \nmm{\biguplus_\subbox{t \in \fOT{s}} \fvars{t}} to get the left side of the implication (independent from these values), immediately broken into
 	\begin{gather}
@@
 \item[\goal{2}:] Let \(\sigma_1: V_1 \uplus \fvars{t_1} \to \values\) and \(\sigma_3: V_3 \to \values\).
-	We use dummy values for variables in \nmm{\biguplus_\subbox{z \in Z} \fvars{t_{3z}}} to get the left side of this implication as an hypothesis (independant from these values):
+	We use dummy values for variables in \nmm{\biguplus_\subbox{z \in Z} \fvars{t_{3z}}} to get the left side of this implication as an hypothesis (independent from these values):
 	\[ \sigma_1 \uplus \sigma_3 \vdash R\mpar{s_1, s_3} \wedge g_1 \hyp{4} \]
@@
 	\end{gather}
-	We use dummy values for variables in \nmm{\biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1}} to get the left side of this implication as an hypothesis (independant from these values):
+	We use dummy values for variables in \nmm{\biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1}} to get the left side of this implication as an hypothesis (independent from these values):
 	\[ \sigma_1 \uplus \sigma_3 \vdash R\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \hyp{9} \]
@@
 	We also name \(t_3\) the original transition from \(T_3\).
-	We build the familly of transition generated by the family \(t_{2x}^{x \in X}\):
+	We build the family of transition generated by the family \(t_{2x}^{x \in X}\):
 	\[ t_{23x}^{x \in X} \defobject x \mapsto \choice{
@@
 \item[\goal{2}:] Let \(\sigma: V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \to \values\).
-	We use dummy values for the variables in \nmm{\biguplus_{x \in X} \fvars{t_{23x}}} to get the left side of the implication as an hypothesis (independant from these values):
+	We use dummy values for the variables in \nmm{\biguplus_{x \in X} \fvars{t_{23x}}} to get the left side of the implication as an hypothesis (independent from these values):
 	\[ \sigma \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \hyp{2} \]
@@
 \item[\goal{1}:] Let \nmm{\sigma: V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \to \values}.
-	We use dummy values for the variables in \nmm{\biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}}} to get the left side of the implication (independant from these values), immediately broken into
+	We use dummy values for the variables in \nmm{\biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}}} to get the left side of the implication (independent from these values), immediately broken into
 	\begin{gather}
@@
 	We also name \(t_1\) the original transition from \(T_1\).
-	We build the familly of transition generated by \(t_{13}\):
+	We build the family of transition generated by \(t_{13}\):
 	\[ t_{31x}^{x \in X} \defobject \choice{
@@
 \item[\goal{2}:] Let \(\sigma: V_{21} \uplus V_{31} \uplus \fvars{t_{21}} \to \values\).
-	We use dummy values for the variables in \nmm{\biguplus_{x \in X} \fvars{t_{31x}}} to get the left side of the implication as an hypothesis (independant from these values):
+	We use dummy values for the variables in \nmm{\biguplus_{x \in X} \fvars{t_{31x}}} to get the left side of the implication as an hypothesis (independent from these values):
 	\[ \sigma \vdash R\mpar{s_{21}, s_{31}} \wedge g_{21} \hyp{2} \]
@@
 \item[\goal{1}:] Let \nmm{\sigma: V_{21} \uplus V_{31} \uplus \biguplus_\subbox{t_{31} \in \fOT{s_{31}}} \fvars{t_{31}} \to \values}.
-	We use dummy values for the variables in \nmm{\biguplus_\subbox{t_{21} \in \fOT{s_{21}}} \fvars{t_{21}}} to get the left side of the implication (independant from these values), immediately broken into
+	We use dummy values for the variables in \nmm{\biguplus_\subbox{t_{21} \in \fOT{s_{21}}} \fvars{t_{21}}} to get the left side of the implication (independent from these values), immediately broken into
 	\begin{gather}

### 2021-06-18 2021-Refinement/report.tex
Tracked holes are explained, better renaming

@@
 The composition of open automata is inherited from open pNets as the open automaton generated from the composition on open pNets.
-This means that composition is only defined on open pNets and not directly on open automata. \Quentin{}{Clunky transition}
-Open pNets with the open automaton semantics and equivalence relation introduced in previous work \cite{2007.10770} were sucessfully used to model and verify some properties of applications \cite{qin:01823507, ameurboulifa:01526055} based on BIP (Behaviour-Interaction-Priority) \cite{basu:hal-00722395} and GCM (Grid Component Model) \cite{baude:inria-00323919}.
+This means that composition is only defined on open pNets and not directly on open automata.
+Open pNets with the open automaton semantics and equivalence relation introduced in previous work \cite{henrio:01299562} were sucessfully used to model and verify some properties of applications \cite{qin:01823507, ameurboulifa:01526055} based on BIP (Behaviour-Interaction-Priority) \cite{basu:hal-00722395} and GCM (Grid Component Model) \cite{baude:inria-00323919}.
 However only an equivalence relation was used.
@@
 
-\section{State of the art}\label{sec:sota}
-Previous work % TODO
-
-% \cite{10.1007/3-540-46428-X_19} Bellegarde2000: simulation with action refinement and silent actions working with parallel composition for LTL properties on TS; here we do not do action refinement nor silent actions but it should be done in future work, also behaviour wrt LTL properties should be checked, also our composition is more expressive than parallel compositon as parallel composition
-% \cite{10.1007/978-3-540-70881-0_26} RR5898: LTS, LTL, Deadlock reduction, non-divergence, weak-refinement, synchronised composition: Closer to what we do here, still open automata are more expressive than LTS and composition is more general than sychronised composition
-% \cite{Zhang2014} 703098: 
-% \cite{DIHEGO2020110598} :
-% \cite{DBLP:journals/corr/abs-2007-10770} weak FH:
-%  \cite{10.1145/3372884.3373161} Algorithm and str-FH:
+\section{Related work}\label{sec:sota}
+Previous work on open automata focused on equivalence relations compatible with composition.
+In an article by Hou, Zechen and Madelaine \cite{10.1145/3372884.3373161}, a computable bisimulation is introduced and proved equivalent to the previous bisimulation already introduced.
+In a more recent work by Ameur-Boulifa, Henrio and Madelaine \cite{2007.10770}, a weak version of the bisimulation on open automata is introduced.
+These works differ from ours because the relation introduced in this report is a refinement relation in the form of a simulation and not a bisimulation.
+Also we do not have results as strong as computability neither a weak version able to tackle silent actions.
+
+There are also similar work, introducing refinement relations, on other models than open automata.
+In a chapter by Bellegarde, Julliand and Kouchnarenko \cite{10.1007/3-540-46428-X_19}, a simulation relation on transition systems is introduced.
+This simulation encompass action refinement, is able to deal with silent actions and is compatible with parallel composition.
+Here the refinement relation does not consider action refinement as valid but it should be done in future work.
+Also they check how LTL properties are preserved or combined using ther refinement which we do not do.
+However their model is less expressive: the transition system model is less expressive than open automata and the parallel composition is less expressive than composition on open automata.
+In a later report by Kouchnarenko and Lanoix \cite{10.1007/978-3-540-70881-0_26}, the refinement relation they introduce is on LTS (labelled transition systems).
+Their relation is additionally prevents deadlock and livelocks.
+The compositon is also extended to synchronised composition which is more expressive.
+In our work we also deal with deadlocks but not with livelocks since the latter arise only with silent actions.
+This work is closer than the previous one to what we do here, still open automata are more expressive than LTS and composition is more general than sychronised composition.
+
+A refinement relation on models nearer to open automata is introduced in an article by Zhang, Meng and Lo \cite{Zhang2014}.
+In their article they work with transition systems with variable which makes the state space potentially infinite.
+This aspect is also present in open automata.
+They show how invariants, a notion near to our reachability predicates, are composed.
+By relation on these invariants they introduce several refinement relations.
+We could have done something similar for non-locking composition reachability predicates which are introduced in Section \ref{sec:proofelts}.
+
+On the deadlock prevention aspect, an article by Dihego, Sampaio and Oliveira \cite{DIHEGO2020110598} present a refinement relation on process algebra (translated to LTS).
+This refinement relation is a special case of inheritance and prevents the introduction of deadlocks.
+Their refinement and inheritance are quite the opposite of our refinement in terms of new behaviours.
+They have channels, interfaces, inputs and outputs, which in the open automata model can be compared to action labels, holes and action data for both inputs and outputs.
+Their model have a rich composition as open automata but the introduction of deadlock is already prevented by a well chosen set of composing operations.
+Also their composition is slightly different than the one on open automata because they can cause loops by linking two channels of the same process, where in open automata the composition makes an oriented tree.
+In their model there is an explicit deadlock and a succesful end where in open automata there are no explicit end.
+We define a deadlock as a configuration without possible transition and assume what is a deadlock when comparing the open automata.
+To define their refinement and inheritance relation they use trace and failure semantics, which are weaker than (bi)simulations \cite{10.5555/640428.640430} and could break with open automata compositon.
 
@@
 The transition are not matched because the relation on configurations is a pre-simulation and it is sufficient to ensure it as will be shown in the proof.
-Apart from the matching transitions this is exactly the same explanation as the intuitive definition.
+Apart from the matching transitions, this is exactly the same explanation as the intuitive definition.
 The expected advantage of this formulation is that a SMT should behave better without the quantifiers.
@@
 
-Intuitively the right automaton is a refinement of the left automaton because the left automaton is what happen when there was no bound \(n\) in the right automaton.
+Intuitively the right automaton is a refinement of the left automaton because the left automaton is what happens when there was no bound \(n\) in the right automaton.
 \[ R \defobject \mbrc{\mpar{l, ||} \mapsto \top, \mpar{r, ||} \mapsto \top} \]
@@
 \input{Vending_machine.tex}
+\vspace{3pt}
 \hrule
+\vspace{3pt}
 \input{Open_vending_machine.tex}
@@
 \[ R \defobject \mpar{s_1, s_3} \mapsto \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \]
-\(R\) is a witness of the transitivity, proof is given in \Ludo{Appendix \ref{apx:trans}}{are we supposed to read appendix D before C.2?}.
+\(R\) is a witness of the transitivity, proof is given in Appendix \ref{apx:trans}.
 \end{proofsketch}
@@
 \[ R \defobject \mpar{\mpar{s_{1'}, s_2}, s_1} \mapsto \choice{\reach{A}\mpar{s_{1'}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1 & \text{if } s_{1'} = s_1 \\ \bot & \text{otherwise}} \]
-Where \(y_1 \mapsto y_{1'}\) is the renaming for object of \(A_1\) in \(A\).
+Where \(y_1 \mapsto y_{1'}\) is the renaming for \(y\) a variable or a valuation of \(A_1\) in \(A\).
 \(R\) is a witness of the limited composition correctness, proof is given in Appendix \ref{apx:lchs}.
@@
 \section{Refinement relation for open automata}\label{sec:refinement}
-One of the \Ludo{solutions}{il manque les paragraphes qui presentent le probleme} to keep transitivity and constraints on holes actions from same holes is to keep track of which holes are in common at each step of refinement.
+One solution to solve the issue presented at the end of previous section, that is to keep transitivity and constraints on holes actions from same holes, is to keep track of which holes are in common at each step of refinement.
 The transitive refinement will have to either rename the holes without constraints or explicitly say which holes have constraints.
@@
 \end{multline*}
-\Ludo{major questions}{il me semble qu il y a plein de trucs qu on comprend pas ici: que se passe t il si H est empty?
-on peut creer un rafinement qui fait n importe quoi avec les trous?
-on ne perd aucune propriete?
-peut etrer qu il manque juste un paragraphe qui explique l approche ses points forts et ses limitations mais l j ai pas l intuition}
 Giving \(R\) and \(H\) is sufficient to characterise the refinement, so we call \(\mpar{R, H}\) a hole-tracking simulation of \(A_1\) by \(A_2\).
+Hole in \(H\) are called tracked holes.
 \end{defi}
-It is basically the same definition as the refinement relation deduced from hole-\(\triangle\) simulations.
 \(R\) is a kind of hole-\(\triangle\) simulation but without the \(\triangle\) constraint on hole sets.
@@
 
-The transitivity property becomes \(\wrel{A}{B}{X} \wedge \wrel{B}{C}{Y} \implies \wrel{A}{C}{X \cap Y}\).
+This definition is close to the refinement relation deduced from hole-\(\triangle\) simulations.
+Actually the latter are particular cases of this one.
+Let \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\) be two open automata.
+If \(J_1 = J_2\), we have \(\wrel{A_1}{A_2}{J_1}\) if and only if there is a hole-equal simulation of \(A_1\) by \(A_2\).
+If \(J_1 \subseteq J_2\), we have \(\wrel{A_1}{A_2}{J_1}\) if and only if there is a hole-subset simulation of \(A_1\) by \(A_2\).
+Finally if \(J_1 \supseteq J_2\), we have \(\wrel{A_1}{A_2}{J_2}\) if and only if there is a hole-superset simulation of \(A_1\) by \(A_2\).
+
+For the open automata refinement, the transitivity property becomes \(\wrel{A}{B}{X} \wedge \wrel{B}{C}{Y} \implies \wrel{A}{C}{X \cap Y}\).
 It behaves the same as if the holes outside the intersection were renamed to avoid conflicts in the first place.
-This makes the combination of the transitivity proofs of hole-\(\triangle\) simulation sufficient to prove \Ludo{transitivity}{lu comme ca c est surprenant: ca semble dire que les restrictions sur les trous de la sec precedente ne sont pas vraiment utiles pour prouver la transitivite}.
+This in combination with the fact that hole-\(\triangle\) simulation are a particular case of hole-tracking simulation makes the combination of the transitivity proofs of hole-\(\triangle\) simulation sufficient to prove transitivity.
 
@@
 The other interesting properties left to check are correctness w.r.t.\@ composition, context refinement, composition congruence and compatibility with FH-bisimulation.
-Proving them for the open automata refinement will also prove them for each hole-\(\triangle\) simulation as they are just restricted cases.
-\begin{thm} Open automata refinement is correct w.r.t.\@ composition \end{thm}
+Some have to be slightly modified for the open automata refinement because of the tracked holes set.
+Proving them for the open automata refinement will also prove them for each hole-\(\triangle\) simulation as they are just particular cases.
+\begin{thm} Open automata refinement is correct w.r.t.\@ composition. \end{thm}
 \begin{proof}
@@
 \end{proof}
-\begin{thm}[Context refinement] Open automata refinement is context refining. \end{thm}
+\begin{thm}[Context refinement] Open automata refinement is context refining when the composition happens in a tracked hole. \end{thm}
 \begin{proofsketch}
@@
 \end{align*}
-Where \(y_3 \mapsto y_{3x}\) is the renaming for object of \(A_3\) in \(A_x\subst{A_3}{k}\).
+Where \(y_3 \mapsto y_{3x}\) is the renaming for \(y\) a variable or a valuation of \(A_3\) in \(A_x\subst{A_3}{k}\).
 \(\mpar{R, H}\) is a witness of \(\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{H}\), proof is given in Appendix \ref{apx:cr}.
 \end{proofsketch}
-\begin{thm}[Composition congruence] Open automata refinement is congruent for composition \end{thm}
+\begin{thm}[Composition congruence] Open automata refinement is congruent for composition. \end{thm}
 \begin{proofsketch}
@@
 \end{align*}
-Where \(y_1 \mapsto y_{1x}\) is the renaming for object of \(A_1\) in \(A_1\subst{A_x}{k}\).
+Where \(y_1 \mapsto y_{1x}\) is the renaming for \(y\) a variable or a valuation of \(A_1\) in \(A_1\subst{A_x}{k}\).
 \(\mpar{R, H}\) is a witness of \(\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{H}\), proof is given in Appendix \ref{apx:cong}.
@@
 \[ R \defobject \mpar{\mpar{s_{1'}, s_2}, s_1} \mapsto \choice{\reach{A}\mpar{s_{1'}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1 & \text{if } s_{1'} = s_1 \\ \bot & \text{otherwise}} \]
-Where \(y_1 \mapsto y_{1'}\) is the renaming for object of \(A_1\) in \(A\).
+Where \(y_1 \mapsto y_{1'}\) is the renaming for \(y\) a variable or a valuation of \(A_1\) in \(A\).
 We want to prove that \(R\) is a hole-subset simulation of \(A\) by \(A_1\).
@@
 \item[1)] \(J = J_2 \uplus J_1 \setminus \mbrc{k} = \emptyset \uplus J_1 \setminus \mbrc{k} \subseteq J_1\)
-\item[2)] We use the fact that \(R\) doesn't constrain the behaviour of \(J_2\) and initial configuration is \Ludo{reachable}{comment on construit la premiere disjoint union sachant que sigma 0 est l union de simga 01 et sigma 02???}:
+\item[2)] We use the fact that \(R\) doesn't constrain the behaviour of \(J_2\) and initial configuration is reachable:
 	\begin{align*}
@@
 	\goal{2c} is exactly \hyp{6c}.
-	We prove \goal{2d} with valuation \(\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}\) for the branch \(s_2\) using \hyp{5d} and \hyp{6d}:
+	We prove \goal{2d} with valuation \(\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}\) for the branch \(s_2\) using \hyp{5d} and \hyp{6d}, more details on why the manipulations are possible are in the proof for transitivity of FH-bisimulation \cite{2007.10770}:
 	\begin{align*}
@@
 \end{align*}
-Where \(y_3 \mapsto y_{3x}\) is the renaming for object of \(A_3\) in \(A_{x3}\).
+Where \(y_3 \mapsto y_{3x}\) is the renaming for \(y\) a variable or a valuation of \(A_3\) in \(A_{x3}\).
 We want to prove that \(\mpar{R, H}\) is a witness of \(\wrel{A_{13}}{A_{23}}{H}\).
@@
 \end{align*}
-Where \(y_1 \mapsto y_{1x}\) is the renaming for object of \(A_1\) in \(A_{x1}\).
+Where \(y_1 \mapsto y_{1x}\) is the renaming for \(y\) a variable or a valuation of \(A_1\) in \(A_{x1}\).
 We want to prove that \(\mpar{R, H}\) is a witness of \(\wrel{A_{21}}{A_{31}}{H}\).

### 2021-06-18 2021-Refinement/report.tex
Final modifs

@@
 \usetikzlibrary{external}
-\usepackage[colorlinks]{hyperref}
+\usepackage[final,hidelinks]{hyperref}
 \AtBeginDocument{\renewcommand\setminus{\smallsetminus}}
@@
 
-There are also similar work, introducing refinement relations, on other models than open automata.
+Some related work on other models than open automata introduce refinement relations.
 In a chapter by Bellegarde, Julliand and Kouchnarenko \cite{10.1007/3-540-46428-X_19}, a simulation relation on transition systems is introduced.
@@
 \(R\) is a kind of hole-\(\triangle\) simulation but without the \(\triangle\) constraint on hole sets.
-On top of that every actions of the holes outside \(H\) is unconstrained in the related automata.
+On top of that every action of the holes outside \(H\) is unconstrained in the related automata.
 
@@
 
-For the open automata refinement, the transitivity property becomes \(\wrel{A}{B}{X} \wedge \wrel{B}{C}{Y} \implies \wrel{A}{C}{X \cap Y}\).
-It behaves the same as if the holes outside the intersection were renamed to avoid conflicts in the first place.
+The idea behind the set of tracked holes is that a tracked hole is guaranteed to behave well with composition.
+To have guarantees on a hole when performing successive refinement we must keep the hole tracked in every refinement step.
+Otherwise everything happens as if the hole of the most refined automaton is not the same as the one with the same name in the least refined automaton.
+It shouldn't be surprising if at some refinement step all the constraints on a hole are lost, that in the whole process they also are.
+It is the best we can do and if someone want to keep the constraint, then they should choose wisely the intermediate automata used for the refinement.
+
+In terms of transitivity, for the open automata refinement, the strongest property we can prove becomes \(\wrel{A}{B}{X} \wedge \wrel{B}{C}{Y} \implies \wrel{A}{C}{X \cap Y}\).
+For a weaker property we can use the fact that \(\wrel{A_1}{A_2}{H} \implies \wrel{A_1}{A_2}{H'}\) when \(H' \subseteq H\).
+Transitivity behaves the same as if the holes outside the intersection were renamed to avoid conflicts in the first place.
 This in combination with the fact that hole-\(\triangle\) simulation are a particular case of hole-tracking simulation makes the combination of the transitivity proofs of hole-\(\triangle\) simulation sufficient to prove transitivity.
@@
 The example also shows a property worth mentioning.
-The holes not looked at (or untracked) are equivalent to having the any action automaton (center of Figure \ref{fig:sevpathref}) composed.
+The holes not tracked are equivalent to having the any action automaton (center of Figure \ref{fig:sevpathref}) composed.
 Actually all the previous refinement are both ways: we can compose the any action automaton in hole \(r\) of the parallel composition to get the other way of the refinement with the identity on holes by composition correctness, and we transform the transition from the identity on holes into the one of the handshake composition by hole-superset refinement.
@@
 The other interesting properties left to check are correctness w.r.t.\@ composition, context refinement, composition congruence and compatibility with FH-bisimulation.
-Some have to be slightly modified for the open automata refinement because of the tracked holes set.
+They have to be slightly modified because of the tracked holes set.
 Proving them for the open automata refinement will also prove them for each hole-\(\triangle\) simulation as they are just particular cases.
-\begin{thm} Open automata refinement is correct w.r.t.\@ composition. \end{thm}
+\begin{thm}
+Open automata refinement is correct w.r.t.\@ composition.
+The tracked holes are the holes of the base automaton minus the composed hole.
+\end{thm}
 \begin{proof}
@@
 \end{proof}
-\begin{thm}[Context refinement] Open automata refinement is context refining when the composition happens in a tracked hole. \end{thm}
+\begin{thm}[Context refinement]
+Open automata refinement is context refining when the composition happens in a tracked hole:
+Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\).
+Let \(\mpar{R_{12}, H_{12}}\) be a hole-tracking simulation of \(A_1\) by \(A_2\), \(k \in H_{12}\) and \(\reach{A_1\subst{A_3}{k}}\) be a witness that \(A_1\subst{A_3}{k}\) is non-locking.
+Let \(H \defobject J_3 \uplus H_{12} \setminus \mbrc{k}\).
+We have \(\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{H}\).
+\end{thm}
 \begin{proofsketch}
-For three open automata \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\), let \(\mpar{R_{12}, H_{12}}\) be a hole-tracking simulation of \(A_1\) by \(A_2\), \(k \in H_{12}\) and \(\reach{A_1\subst{A_3}{k}}\) be a witness that \(A_1\subst{A_3}{k}\) is non-locking.
 The idea for the relation on configurations is that \(A_2\) simulates \(A_1\) while \(A_3\) does the same things in both compositions in the hole \(k\).
-\begin{align*}
-	R \defobject & \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_1\subst{A_3}{k}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \\
-	H \defobject & J_3 \uplus H_{12} \setminus \mbrc{k}
-\end{align*}
+\[ R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_1\subst{A_3}{k}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \]
 Where \(y_3 \mapsto y_{3x}\) is the renaming for \(y\) a variable or a valuation of \(A_3\) in \(A_x\subst{A_3}{k}\).
@@
 \end{proofsketch}
-\begin{thm}[Composition congruence] Open automata refinement is congruent for composition. \end{thm}
+\begin{thm}[Composition congruence]
+Open automata refinement is congruent for composition:
+Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\).
+Let \(k \in J_1\), \(\mpar{R_{23}, H_{23}}\) be a hole-tracking simulation of \(A_2\) by \(A_3\) and \(\reach{A_1\subst{A_2}{k}}\) be a witness that \(A_1\subst{A_2}{k}\) is non-locking.
+Let \(H \defobject H_{23} \uplus J_1 \setminus \mbrc{k}\).
+We have \(\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{H}\).
+\end{thm}
 \begin{proofsketch}
-For three open automata \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\), let \(k \in J_1\), \(\mpar{R_{23}, H_{23}}\) be a hole-tracking simulation of \(A_2\) by \(A_3\) and \(\reach{A_1\subst{A_2}{k}}\) be a witness that \(A_1\subst{A_2}{k}\) is non-locking.
 The idea for the relation on configurations is that \(A_3\) simulates \(A_2\) while \(A_1\) does the same things in both compositions.
-\begin{align*}
-	R \defobject & \mpar{\mpar{s_{12}, s_2}, \mpar{s_{13}, s_3}} \mapsto \choice{R_{23}\mpar{s_2, s_3} \wedge \reach{A_1\subst{A_2}{k}}\mpar{s_{12}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{12} = v_{13} & \text{if } s_{12} = s_{13} \\ \bot & \text{otherwise}} \\
-	H \defobject & H_{23} \uplus J_1 \setminus \mbrc{k}
-\end{align*}
+\[ R \defobject \mpar{\mpar{s_{12}, s_2}, \mpar{s_{13}, s_3}} \mapsto \choice{R_{23}\mpar{s_2, s_3} \wedge \reach{A_1\subst{A_2}{k}}\mpar{s_{12}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{12} = v_{13} & \text{if } s_{12} = s_{13} \\ \bot & \text{otherwise}} \]
 Where \(y_1 \mapsto y_{1x}\) is the renaming for \(y\) a variable or a valuation of \(A_1\) in \(A_1\subst{A_x}{k}\).

### 2021-06-18 2021-Refinement/report.tex
Last typos before sending the report

@@
 
-Refinement relations verifies that and implementation satisfies some properties with respect to a specification.
+Refinement relations verify that and implementation satisfies some properties with respect to a specification.
 The open pNets model is based around a hierarchical composition of generalised automata.
-A properties a refinement can check on them is the non introduction of deadlocks.
+A property a refinement can check on them is the non introduction of deadlocks.
 A deadlock being an unintended state where no further action is possible.
@@
 \item The characterisation of a composition that doesn't introduce deadlocks.
-\item The introduciton of several refinement relations for open automata that behave nicely with composition.
+\item The introduction of several refinement relations for open automata that behave nicely with composition.
 \end{enumerate}
@@
 In a later report by Kouchnarenko and Lanoix \cite{10.1007/978-3-540-70881-0_26}, the refinement relation they introduce is on LTS (labelled transition systems).
-Their relation is additionally prevents deadlock and livelocks.
+Their relation additionally prevents deadlock and livelocks.
 The compositon is also extended to synchronised composition which is more expressive.
@@
 They have channels, interfaces, inputs and outputs, which in the open automata model can be compared to action labels, holes and action data for both inputs and outputs.
-Their model have a rich composition as open automata but the introduction of deadlock is already prevented by a well chosen set of composing operations.
+They have a rich composition as open automata but the introduction of deadlock is already prevented by a well chosen set of composing operations.
 Also their composition is slightly different than the one on open automata because they can cause loops by linking two channels of the same process, where in open automata the composition makes an oriented tree.
-In their model there is an explicit deadlock and a succesful end where in open automata there are no explicit end.
+In their model there is an explicit deadlock and a succesful termination where in open automata there are no explicit termination.
 We define a deadlock as a configuration without possible transition and assume what is a deadlock when comparing the open automata.

### 2021-06-22 2021-Refinement/report.tex
Proofs in body

@@
 The composition may look like a handshake, with both automata running in parallel (product of states and joint variables) however it is asymmetric because it is the first automaton that decides when the second can evolve, while the first automaton can evolve independently as soon as the hole is not involved in the open transition considered.
-
+\begin{exi}\label{exi:full_comp}
+\begin{figure}
+\centering
+\input{Traffic_Lights_Spec.tex}
+\caption{The specification of a traffic light system}
+\label{fig:tls}
+\end{figure}
+\begin{figure}
+\centering
+\input{Traffic_Lights_Controller.tex}
+\vrule
+\input{Traffic_Lights_Register.tex}
+\caption{On the left: An example of controller agent; On the right: An example of counter agent}
+\label{fig:tlh}
+\end{figure}
+This example is derived and adapted from a traffic light controller in a collection of examples for pNets.
+It is supposed to be a single traffic light.
+
+Figure \ref{fig:tls} shows the light controller with some synchronisation logic.
+It takes an unimplemented control circuit in the hole \(ctl\) which gives the timings and an also unimplemented counter in the hole \(cnt\) to count external \(\act{tick}\) actions.
+The three states are used to remember which colored light is on and this color can be retrieved by the environment by synchronising with the actions \(\act{onXxx}\) (Xxx is either Red, Yellow or Green) if it is not stored externally.
+
+The color switches when the counter and the control circuit agree that the time is over.
+The new time limit can be set by the control circuit and the exposed action to the exterior is a \(\tau\).
+
+The components we choose to compose in the holes are in Figure \ref{fig:tlh}.
+On the left there is the controller agent which will be composed in the hole \(ctl\).
+Its role is to decide the duration before switching the lights.
+This implementation is simply a constant time for each color; we could imagine using a more fancy controller which decides of the time depending on the traffic of each lane.
+
+On the right is the counter agent which will be composed in the hole \(cnt\).
+Its role is to get a target, then count ticks until that target is reached, then emit an action with the elapsed time and restart.
+This implementation does exactly that and forbids any extra tick.
+\begin{figure}
+\centering
+\input{Traffic_Lights_Full.tex}
+\caption{The full traffic lights system}
+\label{fig:tlf}
+\end{figure}
+The automaton on Figure \ref{fig:tlf} is a simplification of the composition of the specification on Figure \ref{fig:tls} and the agents on Figure \ref{fig:tlh}.
+The simplification was hand made because it is a hard problem as explained at the end of Section \ref{sec:comp}.
+It consisted in removing unreachable states, reducing the size of the guard and reducing the amount of variables.
+Otherwise the figure would have 36 states (\(3 \times 2 \times 6\)) but only 6 reachable from the initial configuration.
+The simplified transitions are the following (where \(n, n+1\) stands for numbers between 1 and 6, Xxx is either Red, Yellow or Green and \(\mpar{Y, X}\) is accordingly \(\mpar{Y, R}\), \(\mpar{R, G}\) or \(\mpar{G, Y}\)):
+\begin{itemize}
+\item \nmm{\OT{XnS}{X(n+1)C}{\tau}{\mbrc{}}{\top}{\mbrc{t \gets k, c \gets 0}}} which is the composition of \nmm{\OT{X}{X}{\tau}{\mbrc{ctl \mapsto \theta\mpar{x}, cnt \mapsto \act{set}\mpar{x}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{S}{C}{\act{set}\mpar{x}}{\mbrc{}}{\top}{\mbrc{t \gets x, c \gets 0}}} from the counter and \nmm{\OT{n}{n+1}{\theta\mpar{k}}{\mbrc{}}{\top}{\mbrc{}}} from the controller.
+\item \nmm{\OT{XnC}{XnC}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} which is the composition of \nmm{\OT{X}{X}{\act{tick}}{\mbrc{cnt \mapsto \act{tick}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} from the counter.
+\item \nmm{\OT{YnC}{X(n+1)S}{\act{TurnXxx}}{\mbrc{}}{c = t}{\mbrc{}}} which is the composition of \nmm{\OT{Y}{X}{\act{TurnXxx}}{\mbrc{cnt \mapsto \act{over}\mpar{x}, ctl \mapsto \delta\mpar{x}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{C}{S}{\act{over}\mpar{c}}{\mbrc{}}{c = t}{\mbrc{}}} from the counter and \nmm{\OT{n}{n+1}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} from the controller.
+\end{itemize}
+To illustrate composition, hand made simplifications and value passing, the \(\tau\) transition from the state \(R\) will be examined.
+The transition in the specification is \nmm{\OT{R}{R}{\tau}{\mbrc{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}.
+The composition can produce 12 states containing the \(R\) state, these states are in \(\mbrc{R} \times \mdbrk{1; 6} \times \mbrc{S, C}\), however only \(R1S\) and \(R2C\) are reachable so we will only consider \(\tau\) transitions from these two.
+The holes \(cnt\) and \(ctl\) are both involved in the \(\tau\) transition and filled with automata so the composed automata must synchronise with a transition.
+
+In the state \(R2C\) the composition produces 2 transitions by composition out of the \(\tau\) transition but both have a false guard; It is still interesting to look at one of them to show the product of composition without simplification.
+
+\nmm{\OT{R2C}{R3C}{\tau}{\mbrc{}}{\top \wedge \top \wedge c < t \wedge \act{set}\mpar{x} = \act{tick} \wedge \theta\mpar{x} = \delta\mpar{x_C}}{\mbrc{c \gets c + 1}}} is made with \nmm{\OT{2}{3}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} from the controller and \nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} from the counter.
+Obviously the equality of actions in the guard cannot be satisfied so the guard is false, it is equivalent to have no transition.
+We could go on to another transition but something worth explaining happened to build its guard.
+The first two \(\top\) come from the guards of the specification and the controller.
+\(c < t\) comes from the counter.
+The rest of the guard comes from the equality constraint between holes actions and automata actions.
+When composing this expression, we can see that the \(x\) variables from the specification, the controller and the counter are in conflict.
+To resolve the conflict, the conflicted variables were renamed depending on where they come from.
+
+In the state \(R1S\) the composition produces 1 transition out of the \(\tau\) transition.
+The simplified transition follows the first pattern in the transitions described before.
+Examining the composition process can illustrate how value passing work.
+The obtained guard is \(\top \wedge \top \wedge \top \wedge \theta\mpar{x} = \theta\mpar{17} \wedge \act{set}\mpar{x} = \act{set}\mpar{x_R}\) and the obtained variable assignment is \(\mbrc{t \gets x_R, c \gets 0}\).
+We can see how value passing works in the equality constraints: the only possible value of \(x\) and \(x_R\) making the guard hold is \(17\), this value has been synchronised from the controller to \(x\) then to the second occurrence of \(x\) to the distinct \(x\) of the counter.
+Note that \nmm{\OT{S}{C}{\act{set}\mpar{t}}{\mbrc{}}{\top}{\mbrc{c \gets 0}}} wouldn't have worked as a transition for the controller because \(t\) is not a transition variable, its value is fixed before the transition and cannot be set outside of the variable update, hence the use of an auxiliary variable \(x\).
+\end{exi}
 Composition is a complex process that generates big automata with complex and potentially simplifiable transitions.
 However simplification is a hard problem that is not yet automatised on open automata, so from this point the guards and transitions will always be simplified by hand without further explanation.
-An example of composition can be found in Appendix \ref{apx:composition}.
 \begin{prop}[Simultaneous composition]
@@
 \end{lem}
-Proof of the lemma is given in Appendix \ref{apx:lemdred}.
-
-Unfortunately, in the general case, this property is conflicting with the properties about the relation on automata because every property involving composition would be applicable on composition introducing deadlocks.
-
-\subsection{Issue with deadlock reduction and composition}
-A way to solve the conflict between deadlock reduction and the properties involving composition is to only consider a composition that do not introduce deadlocks.
-With this new condition on validity of composition we are able to define in the next sections a refinement relation where most of the properties of interest are satisfied.
-
-Before characterising a composition which does not introduce deadlocks we need to be able to tell which states are reachable because some deadlocks are not reachable and should not be taken into account as being introduced.
-\begin{defi}[Reachability]
-For any open automata \(A \defobject \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is a predicate on states satisfying both
-\defitem Inital state is reachable: \(\sigma_0 \vdash \reach{A}\mpar{s_0}\)
-\defitem Reachability is preserved across transitions: \nmm{\forall t \defobject \OTg \in T, \fvars{t} \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}}
-\end{defi}
-The reachability predicate is used to characterise the reachable configurations in a run of an automaton.
-In fact the role of the predicate is to characterise potentially reachable configurations without having to characterise configurations as the result of a valid path in an automaton.
-
-To do that we impose that the initial configuration is reachable and that reachability is preserved by taking valid transitions.
-This effectively makes reachability take into account all paths, and potentially over-approximate the reachable configurations.
-The exact reachability may not be representable in the formulas, hence the need of potentially over-approximating.
-\begin{defi}[Non-locking composition, intuitive definition]
-Let \(A_i \defobject \OAg[i], 0 \leq i \leq n\).
-The composition \(A \defobject A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is non-locking if \(A\) has a reachability predicate satisfying:
-From reachable configurations, if there was a possible transition in \(A_0\) then there is a possible transition in \(A\).
-Formally for \(\OAg \defobject A\), it gives
-\begin{multline*}
-	\forall s \defobject \mpar{s'_i}_{0 \leq i \leq n} \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A}\mpar{s}} \implies \\
-	\mpar{\exists t_0 \in \fOT{s'_0}, \exists \nu_0: \fvars{t_0} \to \values, \sigma \uplus \nu_0 \vdash \fguard{t_0}} \implies \\
-	\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t}
-\end{multline*}
-\end{defi}
-As in the previous section, the definition can be simplified into a less intuitive version:
-\begin{defi}[Non-locking composition, working definition]
-\(A \defobject A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is a non-locking composition if:
-\[ \forall s \defobject \mpar{s_0, s'} \in S, V \uplus \biguplus_\subbox{t_0 \in \fOT{s_0}} \fvars{t_0} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_0 \in \fOT{s_0}} \fguard{t_0} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
-\end{defi}
-\begin{lem}\label{lem:nlced}
-The intuitive and working definition of non-locking composition are equivalent.
-\end{lem}
-An illustration of both the introduction of a deadlock by composition and the definition of non-locking composition is given in Appendix \ref{apx:lockcomp}.
-Proof of the lemma is given in Appendix \ref{apx:lemnlced}.
-
-This new definition of composition can replace the standard composition.
-We may think that if the simultaneous composition is non-locking, then for every composition order, each composition step is non-locking.
-Unfortunately it is not true.
-This happens because in an intermediate composition step, a state can become a deadlock, but in a further composition step it would become unreachable.
-% However the opposite way is true: % Would need a proof, non-trivial
-% If there is an order of composition where every composition is non-locking then the last composition is non-locking, last composition resulting in the same automaton as the simultaneous composition.
-% So the condition is better checked after the simultaneous composition or the last individual composition.
-\begin{exi}
-\begin{figure}
-\centering
-\input{file_sync.tex}
-\caption{A made-up protocol for file synchronisation}
-\label{fig:pnls}
-\end{figure}
-The automaton on Figure \ref{fig:pnls} is a sample protocol for file synchronisation.
-The two holes are \(net\) a process to manage network communications, and \(hash\) a process to check files integrity.
-The state \(i\) is the initial state.
-In that state we want to synchronise the files before working, or work on the local version as a fallback.
-If the preferred version is the remote one, we go in state \(d1\) asking the network manager to fetch the latest version, then ask the integrity checker to validate the files.
-If the preferred version is the local one, we go in state \(d2\) asking for the integrity checker to validate the local files, then ask the network manager to push them.
-In fallback we use the local version.
-
-We can plug an inactive process for the network manager and the file integrity checker by composing a deadlock automaton in their holes, but always both at the same time.
-The reason for that is the simultaneous composition is non-locking, but any individual composition is locking because either the state \(d1\) or \(d2\) (depending on the order) is reachable and becomes a deadlock.
-\end{exi}
-From this point and when checking the refinement properties, composition will only refer to non-locking composition.
-
-\section{Refinement relations in restricted cases}\label{sec:prelref}
-With all these properties explained, we can look at some concrete refinement relations.
-The main goal of this section is to explain the different aspects of refinement in restricted cases so that they are not all introduced at once in the real refinement relation.
-In particular if we have a family of open automata \(A_i \defobject \OAg[i]\), \(0 \leq i \leq n\), let \(A \defobject A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\).
-Recall that there is no relation between the holes of \(A\) and \(A_0\) because \(\mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}\) is neither subset nor superset of \(J_0\).
-So looking at restricted cases where holes are related in a specific manner can help understanding the general case.
-Hopefully the intermediate refinement relation introduced can be used as simpler (and less expensive to compute) versions of the real refinement relation in the case the manipulated automata respect some constraints.
-
-We restrict the holes of the related automata so that we can explain the different refinements without their interactions.
-In the following definition, \(\triangle \in \mbrc{\subseteq, =, \supseteq}\).
-\begin{defi}[Hole-\(\triangle\) simulation]
-For two open automata \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\triangle\) simulation of \(A_1\) by \(A_2\) if:
-\item[1)] \(J_1 \triangle J_2\)
-\item[2)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
-\item[3)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)\vspace{-8pt}
-\noindent\begin{multline*}
-	\mpar{\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
-		\quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
-		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}}
-	\end{array}} \\
-	\wedge \mpar{V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
-\end{multline*}
-\end{defi}
-The third item of the definition has two parts:
-The first part is the main requirement, a stronger version of the pre-simulation requirement so that it better fits SMT.
-Instead of matching an instanciated transition to another instanciated transition as in the pre-simulation definition, we match an open transition to a family of covering open-transitions.
-The second part is directly the deadlock reduction requirement.
-
-The hole-equal simulation is applicable when the related automata have the same holes.
-It is designed to capture all the refinements other than composition: Duplicating and merging states and transitions, changing variables, removing transitions, adding requirements to guards, specifying more initial variables, and many more.
-
-The hole-subset simulation is applicable when the simulated automaton has less holes.
-It is designed to have composition correctness when the composed automata have no holes.
-
-The hole-superset simulation is applicable when the simulated automaton has more holes.
-It is designed to capture the addition of holes involved in transitions, which will indirectly add requirements to transitions when the new holes will be composed.
-It is also an attempt at giving a meaning to the new holes when composing with any open automata.
-However it does not capture the removal of holes because other issues arise when trying to both add and remove holes.
-\begin{exi}[Example of hole-equal simulation]
-\begin{figure}
-\centering
-\input{parallel_comp.tex}
-\vrule
-\input{n_control_switch.tex}
-\caption{On the left: Parallel composition operator; On the right: n control switches automaton}
-\label{fig:hisim}
-\end{figure}
-Figure \ref{fig:hisim} introduces two related open automata with same holes \(\mbrc{l, r}\).
-The automaton on the left is a parallel composition: any hole can perform actions at any time, the actions are passed unmodified and no synchronisation is performed.
-The automaton on the right is a sequential composition with \(n\) control switches: a hole performs a sequence of actions then the other does, there are \(n\) sequences of a single automaton doing actions without the other performing some.
-
-Intuitively the right automaton is a refinement of the left automaton because the left automaton is what happens when there was no bound \(n\) in the right automaton.
-\[ R \defobject \mbrc{\mpar{l, ||} \mapsto \top, \mpar{r, ||} \mapsto \top} \]
-\(R\) is a hole-identical simulation of \(n\) control switches by parallel composition.
-There are enough examples of proofs of refinement in this report for the reader to be able to prove it as an exercise.
-\end{exi}
-\begin{exi}[Example of hole-subset simulation]
-Example of Appendix \ref{apx:composition} can be reused here.
-The automaton on Figure \ref{fig:tlf} is a refinement of the one on Figure \ref{fig:tls} by limited composition correctness (Proposition \ref{prop:cc'} below).
-
-It is a simplified version of the motivation for making a refinement relation, which is the traffic light system in an article about weak-bisimulation \cite{wang:03126313}.
-It had to be modified because here the simulation is a strong-simulation (no silent actions).
-\end{exi}
-\begin{exi}[Example of hole-superset simulation]
-\begin{figure}
-\centering
-\input{Vending_machine.tex}
-\vspace{3pt}
-\hrule
-\vspace{3pt}
-\input{Open_vending_machine.tex}
-\caption{On the top: Vending machine; On the bottom: Open vending machine}
-\label{fig:ovm}
-\end{figure}
-Figure \ref{fig:ovm} introduces two related open automata with same states and transitions except for hole actions.
-Both automata are vending machine: Money is introduced while in state \(I\), accumulating in the money variable \(m\), when there are enough money a coffee or a tea can be ordered by taking the transitions to the states \(C\) or \(T\) and money is decreased, then the drink is served by taking the transition back to state \(I\).
-The holes added in the open version on the bottom are \(mon\) a hole which task is to verify the money inserted (coin vary depending on the country for instance) and \(serv\) which task is to serve the drink and report the exact amount served.
-
-The automaton on the bottom is a refinement of the automaton on the top using hole-superset simulation.
-The relation on states is the same as the one for reflexivity.
-Intuitively the automaton on the bottom binds some variables to action produced by the holes, the automaton is no more free to take a transition some hole is not able to perform.
-For instance if the automaton in the hole \(mon\) can only perform \(\act{credit}\mpar{100}\) then after the composition, the automaton on the bottom should be a refinement of the one on the top.
-Actually after such a composition it is still in hole-superset simulation with the top automaton by Proposition \ref{prop:cc'}.
-\end{exi}
-\begin{thm} A hole-\(\triangle\) simulation is a pre-simulation. \end{thm}
-Proof is given in Appendix \ref{apx:presim}.
-\begin{thm} The hole-\(\triangle\) simulation on automata is a preorder. \end{thm}
-\begin{proofsketch}
-The idea for reflexivity is that the related automata are always in the same configuration.
-\[ R \defobject \mpar{s, s'} \mapsto \choice{\bigwedge_{v \in V} v_1 = v_2 & \text{if } s = s'\\ \bot & \text{otherwise}} \]
-Where \(v_x\) is the renaming to distinguish conflicting automaton variables.
-\(R\) is a witness of the reflexivity, the proof is mainly the same as several of the following ones so it will be omitted.
-
-For transitivity we need to introduce thee open automata.
-Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) be open automata.
-Let \(R_{12}\) be a hole-\(\triangle\) simulation of \(A_1\) by \(A_2\) and \(R_{23}\) of \(A_2\) by \(A_3\).
-The idea for \(R\) is that there exists a state \(s_2 \in S_2\) and values for \(V_2\) such that \(R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}\).
-However we cannot talk about states in formulas.
-The solution is to expand the existential quantifier on states as we did in deadlock reduction, which is possible because states are finite.
-\[ R \defobject \mpar{s_1, s_3} \mapsto \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \]
-\(R\) is a witness of the transitivity, proof is given in Appendix \ref{apx:trans}.
-\end{proofsketch}
-\begin{prop}[Limited composition correctness]\label{prop:cc'} Hole-subset simulation is correct w.r.t.\@ composition with automata without holes. \end{prop}
-\begin{proofsketch}
-For two open automata \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\) with \(J_2 = \emptyset\), let \(k \in J_1\) and \(A \defobject A_1\subst{A_2}{k}\).
-Let \(\reach{A}\) be a witness that the composition producing \(A\) is non-locking.
-The idea for the relation on configurations is that the copy of \(A_1\) in \(A\) do the same things as \(A_1\), as if we were trying to prove reflexivity.
-\[ R \defobject \mpar{\mpar{s_{1'}, s_2}, s_1} \mapsto \choice{\reach{A}\mpar{s_{1'}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1 & \text{if } s_{1'} = s_1 \\ \bot & \text{otherwise}} \]
-Where \(y_1 \mapsto y_{1'}\) is the renaming for \(y\) a variable or a valuation of \(A_1\) in \(A\).
-\(R\) is a witness of the limited composition correctness, proof is given in Appendix \ref{apx:lchs}.
-\end{proofsketch}
-\begin{prop}[Special composition correctness]
-If there is a hole-superset simulation of \(A_1\) by \(A_2\) and \(A_1\subst{A_3}{k}\) is non-locking, then there is a hole-superset simulation of \(A_1\subst{A_3}{k}\) by \(A_2\).
-Where \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\), \(A_3\) are open automata and \(k \in J_1 \setminus J_2\).
-\end{prop}
-\begin{proofsketch}
-Let \(R_{12}\) be a hole-superset simulation of \(A_1\) by \(A_2\) and \(\reach{A_1\subst{A_3}{k}}\) be a witness that \(A_1\subst{A_3}{k}\) is non-locking.
-The idea for the relation on configurations is to combine the non-locking composition and the already existing relation on configurations.
-\[ R \defobject \mpar{\mpar{s_1, s_3}, s_2} \mapsto R_{12}\mpar{s_1, s_2} \wedge \reach{A_1\subst{A_3}{k}}\mpar{s_1, s_3} \]
-\(R\) is a witness of the special composition correctness, proof is given in Appendix \ref{apx:schs}.
-\end{proofsketch}
-The hole-subset simulation can only tell if there is a refinement when the composed automata have no holes.
-To lift this limitation we need to allow adding holes which doesn't have a direct interpretation.
-
-At first a solution using a function mapping the action performed by the new holes in the composition to the ones performed by removed hole in the base automaton was explored.
-It was abandoned because the base automaton has nothing intelligent to tell about the action required by the composed automata.
-That is the reason the hole-superset simulation doesn't constrain the action performed by the added holes.
-The solution adopted is to give a meaning to adding hole and only adding in a simulation.
-With the hole-superset simulation we have an interpretation to added holes:
-They are holes imposing a restriction on the transition variables.
-However with that solution we cannot remove holes so we cannot express composition correctness, hence the need of the special composition correctness for hole-superset simulation.
-
-For composition correctness, using only one of the hole-\(\triangle\) simulations cannot tell that a non-locking composition with any open automaton is a refinement of the base automaton because we need at the same time to add and remove holes.
-If we build the refinement relation as the transitive closure of all the hole-\(\triangle\) simulations then an issue arise.
-The transitivity propriety causes that when a hole present in both extrema of the chain but absent in an intermediate automaton, there is a refinement between the extrema of the chain.
-In that case all the constraint on holes actions are lifted even if we would like to require an equality of these actions on the transitive closure.
-
-\section{Refinement relation for open automata}\label{sec:refinement}
-One solution to solve the issue presented at the end of previous section, that is to keep transitivity and constraints on holes actions from same holes, is to keep track of which holes are in common at each step of refinement.
-The transitive refinement will have to either rename the holes without constraints or explicitly say which holes have constraints.
-\begin{defi}[Open automata refinement]
-For two open automata \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a refinement of \(A_2\) looking at \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), is defined as:
-\begin{multline*}
-	\exists R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2], \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge \forall \mpar{s_1, s_2} \in S_1 \times S_2, \\
-	\mpar{\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\[12pt]
-		\quad \mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H} \\[-10pt]
-		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \\
-			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}} \\
-	\end{array}} \\
-	\wedge V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
-\end{multline*}
-Giving \(R\) and \(H\) is sufficient to characterise the refinement, so we call \(\mpar{R, H}\) a hole-tracking simulation of \(A_1\) by \(A_2\).
-Hole in \(H\) are called tracked holes.
-\end{defi}
-\(R\) is a kind of hole-\(\triangle\) simulation but without the \(\triangle\) constraint on hole sets.
-On top of that every action of the holes outside \(H\) is unconstrained in the related automata.
-
-This definition is close to the refinement relation deduced from hole-\(\triangle\) simulations.
-Actually the latter are particular cases of this one.
-Let \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\) be two open automata.
-If \(J_1 = J_2\), we have \(\wrel{A_1}{A_2}{J_1}\) if and only if there is a hole-equal simulation of \(A_1\) by \(A_2\).
-If \(J_1 \subseteq J_2\), we have \(\wrel{A_1}{A_2}{J_1}\) if and only if there is a hole-subset simulation of \(A_1\) by \(A_2\).
-Finally if \(J_1 \supseteq J_2\), we have \(\wrel{A_1}{A_2}{J_2}\) if and only if there is a hole-superset simulation of \(A_1\) by \(A_2\).
-
-The idea behind the set of tracked holes is that a tracked hole is guaranteed to behave well with composition.
-To have guarantees on a hole when performing successive refinement we must keep the hole tracked in every refinement step.
-Otherwise everything happens as if the hole of the most refined automaton is not the same as the one with the same name in the least refined automaton.
-It shouldn't be surprising if at some refinement step all the constraints on a hole are lost, that in the whole process they also are.
-It is the best we can do and if someone want to keep the constraint, then they should choose wisely the intermediate automata used for the refinement.
-
-In terms of transitivity, for the open automata refinement, the strongest property we can prove becomes \(\wrel{A}{B}{X} \wedge \wrel{B}{C}{Y} \implies \wrel{A}{C}{X \cap Y}\).
-For a weaker property we can use the fact that \(\wrel{A_1}{A_2}{H} \implies \wrel{A_1}{A_2}{H'}\) when \(H' \subseteq H\).
-Transitivity behaves the same as if the holes outside the intersection were renamed to avoid conflicts in the first place.
-This in combination with the fact that hole-\(\triangle\) simulation are a particular case of hole-tracking simulation makes the combination of the transitivity proofs of hole-\(\triangle\) simulation sufficient to prove transitivity.
-
-Not renaming conflicting holes still have an interest.
-If we are trying to build an automaton \(A\) with several constraints \(\wrel{A}{A_i}{J_{Ai}}, i \in I\) (as done in B method \cite{cansell:inria-00099794}) and each \(A_i\) is a refinement of some automaton \(C\) then we can have each \(A_i\) constrain a different subset of \(A\)'s holes.
-On each individual path \(A \leq_{J_{Ai}} A_i \leq_{J_{Ai}} C\), some holes of \(A\) are unconstrained but when considering all path they are all constrained.
-However this doesn't implies \(A \leq_{\bigcup_{i \in I} J_{Ai}} C\), it has to be checked separately.
-\begin{exi}
-\begin{figure}
-\centering
-\input{identity.tex}
-\vrule
-\input{any.tex}
-\vrule
-\input{handshake_comp}
-\caption{On the left: Generic identity on holes; On the center: Any action automaton; On the right: Handshake composition.}
-\label{fig:sevpathref}
-\end{figure}
-We have two refinement paths when \(h\) is replaced by \(l\) and by \(r\) in identity on holes (left of Figure \ref{fig:sevpathref}): the parallel composition (left of Figure \ref{fig:hisim}) is a refinement of the identity on holes, which is a refinement of the handshake composition (right of Figure \ref{fig:sevpathref}).
-However we do not have the parallel composition being a refinement of the handshake composition looking at \(\mbrc{l, r}\).
-
-The example also shows a property worth mentioning.
-The holes not tracked are equivalent to having the any action automaton (center of Figure \ref{fig:sevpathref}) composed.
-Actually all the previous refinement are both ways: we can compose the any action automaton in hole \(r\) of the parallel composition to get the other way of the refinement with the identity on holes by composition correctness, and we transform the transition from the identity on holes into the one of the handshake composition by hole-superset refinement.
-\end{exi}
-The other interesting properties left to check are correctness w.r.t.\@ composition, context refinement, composition congruence and compatibility with FH-bisimulation.
-They have to be slightly modified because of the tracked holes set.
-Proving them for the open automata refinement will also prove them for each hole-\(\triangle\) simulation as they are just particular cases.
-\begin{thm}
-Open automata refinement is correct w.r.t.\@ composition.
-The tracked holes are the holes of the base automaton minus the composed hole.
-\end{thm}
-\begin{proof}
-We will decompose composition into two refinement steps, transitivity will complete the proof.
-Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(k \in J_1\) such that \(A_1\subst{A_2}{k}\) is non-locking.
-We pose \(A'_2\) as \(A_2\) stripped of its holes.
-\begin{align*}
-	A'_2 \defobject & \OA{S_2}{s_{02}}{V_2}{\sigma_{02}}{\emptyset}{T'_2} \\
-	T'_2 \defobject & \mset{\OT{s}{s'}{\alpha}{\mbrc{}}{g}{\psi}}{\OTg \in T_2}
-\end{align*}
-By limited composition correctness we have \(\wrel{A_1\subst{A'_2}{k}}{A_1}{J_1 \setminus \mbrc{k}}\).
-Adding holes and binding actions to the new holes is a refinement for hole-superset simulation so we have \(\wrel{A_1\subst{A_2}{k}}{A_1\subst{A'_2}{k}}{J_1 \setminus \mbrc{k}}\).
-By transitivity we have composition correctness.
-\end{proof}
-\begin{thm}[Context refinement]
-Open automata refinement is context refining when the composition happens in a tracked hole:
-Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\).
-Let \(\mpar{R_{12}, H_{12}}\) be a hole-tracking simulation of \(A_1\) by \(A_2\), \(k \in H_{12}\) and \(\reach{A_1\subst{A_3}{k}}\) be a witness that \(A_1\subst{A_3}{k}\) is non-locking.
-Let \(H \defobject J_3 \uplus H_{12} \setminus \mbrc{k}\).
-We have \(\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{H}\).
-\end{thm}
-\begin{proofsketch}
-The idea for the relation on configurations is that \(A_2\) simulates \(A_1\) while \(A_3\) does the same things in both compositions in the hole \(k\).
-\[ R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_1\subst{A_3}{k}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \]
-Where \(y_3 \mapsto y_{3x}\) is the renaming for \(y\) a variable or a valuation of \(A_3\) in \(A_x\subst{A_3}{k}\).
-\(\mpar{R, H}\) is a witness of \(\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{H}\), proof is given in Appendix \ref{apx:cr}.
-\end{proofsketch}
-\begin{thm}[Composition congruence]
-Open automata refinement is congruent for composition:
-Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\).
-Let \(k \in J_1\), \(\mpar{R_{23}, H_{23}}\) be a hole-tracking simulation of \(A_2\) by \(A_3\) and \(\reach{A_1\subst{A_2}{k}}\) be a witness that \(A_1\subst{A_2}{k}\) is non-locking.
-Let \(H \defobject H_{23} \uplus J_1 \setminus \mbrc{k}\).
-We have \(\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{H}\).
-\end{thm}
-\begin{proofsketch}
-The idea for the relation on configurations is that \(A_3\) simulates \(A_2\) while \(A_1\) does the same things in both compositions.
-\[ R \defobject \mpar{\mpar{s_{12}, s_2}, \mpar{s_{13}, s_3}} \mapsto \choice{R_{23}\mpar{s_2, s_3} \wedge \reach{A_1\subst{A_2}{k}}\mpar{s_{12}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{12} = v_{13} & \text{if } s_{12} = s_{13} \\ \bot & \text{otherwise}} \]
-Where \(y_1 \mapsto y_{1x}\) is the renaming for \(y\) a variable or a valuation of \(A_1\) in \(A_1\subst{A_x}{k}\).
-\(\mpar{R, H}\) is a witness of \(\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{H}\), proof is given in Appendix \ref{apx:cong}.
-\end{proofsketch}
-\begin{thm}[FH-bisimulation compatibility] Open automata refinement is compatible with FH-bisimulation \end{thm}
-\begin{proofsketch} The requirements of FH-bisimulation are strictly stronger than the open automata refinement so using transitivity is sufficient. \end{proofsketch}
-With that last property, every interesting property is proved for the presented refinement relation.
-
-\section{Conclusion}\label{sec:ccl}
-In this report we redefined on open automata an operation from open pNets called composition.
-This operation was defined as the composition of the open pNets used to generate the open automata and not directly on open automata.
-So to reason on composition directly and to better separate the models the definition had to be given without introducing open pNets.
-Then we recalled the main properties expected from a refinement relation on a structure with composition and adapted them to open automata.
-To do that we restricted the composition so that it doesn't introduce deadlocks.
-Then we introduced several refinement relations in restricted cases to avoid dealing immediately with the hard issue of the incomparability of hole sets.
-Finally we introduced a refinement relation having all the interesting properties and dealing with the aforementioned issue at the cost of a slight modification on transitivity.
-
-However the refinement presented here still do not work on the motivating example because of silent actions.
-To be able to refine in the presence of silent action, a weak variant of the simulation is needed.
-This variant will also probably be able to encompass action refinement as a valid refinement because the mechanism are similar.
-
-\pagebreak
-\bibliographystyle{plain}
-\bibliography{biblio}
-
-\pagebreak
-\appendix
-\part*{Appendix}
-
-\section{Example of composition}
-
-\subsection{Complete composition}\label{apx:composition}
-\begin{figure}[h]
-\centering
-\input{Traffic_Lights_Spec.tex}
-\caption{The specification of a traffic light system}
-\label{fig:tls}
-\end{figure}
-\begin{figure}
-\centering
-\input{Traffic_Lights_Controller.tex}
-\vrule
-\input{Traffic_Lights_Register.tex}
-\caption{On the left: An example of controller agent; On the right: An example of counter agent}
-\label{fig:tlh}
-\end{figure}
-This example is derived and adapted from a traffic light controller in a collection of examples for pNets.
-It is supposed to be a single traffic light.
-
-Figure \ref{fig:tls} shows the light controller with some synchronisation logic.
-It takes an unimplemented control circuit in the hole \(ctl\) which gives the timings and an also unimplemented counter in the hole \(cnt\) to count external \(\act{tick}\) actions.
-The three states are used to remember which colored light is on and this color can be retrieved by the environment by synchronising with the actions \(\act{onXxx}\) (Xxx is either Red, Yellow or Green) if it is not stored externally.
-
-The color switches when the counter and the control circuit agree that the time is over.
-The new time limit can be set by the control circuit and the exposed action to the exterior is a \(\tau\).
-
-The components we choose to compose in the holes are in Figure \ref{fig:tlh}.
-On the left there is the controller agent which will be composed in the hole \(ctl\).
-Its role is to decide the duration before switching the lights.
-This implementation is simply a constant time for each color; we could imagine using a more fancy controller which decides of the time depending on the traffic of each lane.
-
-On the right is the counter agent which will be composed in the hole \(cnt\).
-Its role is to get a target, then count ticks until that target is reached, then emit an action with the elapsed time and restart.
-This implementation does exactly that and forbids any extra tick.
-\begin{figure}
-\centering
-\input{Traffic_Lights_Full.tex}
-\caption{The full traffic lights system}
-\label{fig:tlf}
-\end{figure}
-The automaton on Figure \ref{fig:tlf} is a simplification of the composition of the specification on Figure \ref{fig:tls} and the agents on Figure \ref{fig:tlh}.
-The simplification was hand made because it is a hard problem as explained at the end of Section \ref{sec:comp}.
-It consisted in removing unreachable states, reducing the size of the guard and reducing the amount of variables.
-Otherwise the figure would have 36 states (\(3 \times 2 \times 6\)) but only 6 reachable from the initial configuration.
-The simplified transitions are the following (where \(n, n+1\) stands for numbers between 1 and 6, Xxx is either Red, Yellow or Green and \(\mpar{Y, X}\) is accordingly \(\mpar{Y, R}\), \(\mpar{R, G}\) or \(\mpar{G, Y}\)):
-\begin{itemize}
-\item \nmm{\OT{XnS}{X(n+1)C}{\tau}{\mbrc{}}{\top}{\mbrc{t \gets k, c \gets 0}}} which is the composition of \nmm{\OT{X}{X}{\tau}{\mbrc{ctl \mapsto \theta\mpar{x}, cnt \mapsto \act{set}\mpar{x}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{S}{C}{\act{set}\mpar{x}}{\mbrc{}}{\top}{\mbrc{t \gets x, c \gets 0}}} from the counter and \nmm{\OT{n}{n+1}{\theta\mpar{k}}{\mbrc{}}{\top}{\mbrc{}}} from the controller.
-\item \nmm{\OT{XnC}{XnC}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} which is the composition of \nmm{\OT{X}{X}{\act{tick}}{\mbrc{cnt \mapsto \act{tick}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} from the counter.
-\item \nmm{\OT{YnC}{X(n+1)S}{\act{TurnXxx}}{\mbrc{}}{c = t}{\mbrc{}}} which is the composition of \nmm{\OT{Y}{X}{\act{TurnXxx}}{\mbrc{cnt \mapsto \act{over}\mpar{x}, ctl \mapsto \delta\mpar{x}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{C}{S}{\act{over}\mpar{c}}{\mbrc{}}{c = t}{\mbrc{}}} from the counter and \nmm{\OT{n}{n+1}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} from the controller.
-\end{itemize}
-
-To illustrate composition, hand made simplifications and value passing, the \(\tau\) transition from the state \(R\) will be examined.
-The transition in the specification is \nmm{\OT{R}{R}{\tau}{\mbrc{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}.
-The composition can produce 12 states containing the \(R\) state, these states are in \(\mbrc{R} \times \mdbrk{1; 6} \times \mbrc{S, C}\), however only \(R1S\) and \(R2C\) are reachable so we will only consider \(\tau\) transitions from these two.
-The holes \(cnt\) and \(ctl\) are both involved in the \(\tau\) transition and filled with automata so the composed automata must synchronise with a transition.
-
-In the state \(R2C\) the composition produces 2 transitions by composition out of the \(\tau\) transition but both have a false guard; It is still interesting to look at one of them to show the product of composition without simplification.
-
-\nmm{\OT{R2C}{R3C}{\tau}{\mbrc{}}{\top \wedge \top \wedge c < t \wedge \act{set}\mpar{x} = \act{tick} \wedge \theta\mpar{x} = \delta\mpar{x_C}}{\mbrc{c \gets c + 1}}} is made with \nmm{\OT{2}{3}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} from the controller and \nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} from the counter.
-Obviously the equality of actions in the guard cannot be satisfied so the guard is false, it is equivalent to have no transition.
-We could go on to another transition but something worth explaining happened to build its guard.
-The first two \(\top\) come from the guards of the specification and the controller.
-\(c < t\) comes from the counter.
-The rest of the guard comes from the equality constraint between holes actions and automata actions.
-When composing this expression, we can see that the \(x\) variables from the specification, the controller and the counter are in conflict.
-To resolve the conflict, the conflicted variables were renamed depending on where they come from.
-
-In the state \(R1S\) the composition produces 1 transition out of the \(\tau\) transition.
-The simplified transition follows the first pattern in the transitions described before.
-Examining the composition process can illustrate how value passing work.
-The obtained guard is \(\top \wedge \top \wedge \top \wedge \theta\mpar{x} = \theta\mpar{17} \wedge \act{set}\mpar{x} = \act{set}\mpar{x_R}\) and the obtained variable assignment is \(\mbrc{t \gets x_R, c \gets 0}\).
-We can see how value passing works in the equality constraints: the only possible value of \(x\) and \(x_R\) making the guard hold is \(17\), this value has been synchronised from the controller to \(x\) then to the second occurrence of \(x\) to the distinct \(x\) of the counter.
-Note that \nmm{\OT{S}{C}{\act{set}\mpar{t}}{\mbrc{}}{\top}{\mbrc{c \gets 0}}} wouldn't have worked as a transition for the controller because \(t\) is not a transition variable, its value is fixed before the transition and cannot be set outside of the variable update, hence the use of an auxiliary variable \(x\).
-
-\subsection{Composition introducing deadlocks and requirements of non-locking composition}\label{apx:lockcomp}
-\begin{exi}[Deadlocks introduced by composition]
-This example reuses the counter introduced in Figure \ref{fig:tlh}.
-The behaviour of the counter is to count external \(\act{tick}\) actions up to the amount set by action \(\act{set}\mpar{x}\) then to notify the environment that this amount of time elapsed.
-In the traffic light example the clock is not specified, we will introduce deadlocks using a wisely chosen clock specification.
-However the full traffic light will not be used in order to simplify the example, only the counter will be.
-\begin{figure}
-\input{randomtick_clock.tex}
-\vrule
-\input{register_anytick.tex}
-\caption{On the left: A clock which imposes a tick; On the right: A modified version of the counter at figure \ref{fig:tlh}}
-\label{fig:anytick}
-\end{figure}
-The clock on the left side of Figure \ref{fig:anytick} transmits the actions of its hole unchanged until the clock imposes a \(\act{tick}\) on its hole.
-This can model a physical clock, because physical time ticks cannot be delayed.
-
-If the hole cannot handle a \(\act{tick}\) at any time then there is a deadlock, which is the case with our counter.
-The composition of this clock with the counter is given on the left of Figure \ref{fig:deadlock}.
-\begin{figure}
-\input{Composition_deadlock.tex}
-\vrule
-\input{Composition_nolock.tex}
-\caption{On the left: Deadlocks introduced by composition; On the right: No deadlock introduced by composition}
-\label{fig:deadlock}
-\end{figure}
-There are two deadlocks:
-The first is in the state \(1S\), which corresponds to the clock trying to impose a tick when the counter is not set.
-The second is in the state \(1C\), which corresponds to the clock trying to impose a tick when the counter has reached the amount previously set, but not has not yet reported it to the environment.
-These deadlocks could have been in the specification in which case they were intended, but it is not the case here.
-
-The counter on the right of Figure \ref{fig:anytick} is a modification to accept ticks at in any state.
-Composing this modified counter gives the automaton on the right of Figure \ref{fig:deadlock} which has no deadlocks.
-
-We should successfully characterise the second composition as non-locking but fail for the first.
-\begin{itemize}
-\item In the state \(0S\) any valuation is reachable (no initial valuation).
-	In both automata the transition \nmm{\OT{0S}{1S}{\tau}{\mbrc{}}{\top}{\mbrc{}}} has a true guard, hence the first branch of the disjunction holds.
-\item In the state \(0C\), for the left automaton, valuations where \(t \geq c \geq 0 \vee \mpar{t < 0 \wedge c = 0}\) are reachable; for the right automaton, valuations where \(c \geq 0\) are reachable.
-	For all these valuations the transition \nmm{\OT{0C}{1C}{\tau}{\mbrc{}}{\top}{\mbrc{}}} has a true guard, hence the first branch of the disjunction holds.
-\item In the state \(1C\), the same valuations as the ones reachable in \(0C\) are also reachable.
-	In the right automaton the transition \nmm{\OT{1C}{0C}{\act{tick}}{\mbrc{}}{\top}{\mbrc{c \gets c + 1}}} has a true guard.
-	In the left automaton the transition \nmm{\OT{1C}{0C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} covers the cases where \(c < t\).
-	For the other cases (\(c = t \vee t \leq 0 \mbrk{\leq c}\)) there are no transition with a true guard, and in the clock the transition same transition as for the state \(1S\) has a true guard, hence the composition is not non-locking.
-\item In the state \(1S\) any valuation is reachable.
-	In the left automaton, no transition is possible, and in the parent automaton \nmm{\OT{1}{0}{\act{tick}}{\mbrc{H \mapsto \act{tick}}}{\top}{\mbrc{}}} had a true guard, so the composition is not a non-locking composition (we already know it at this point).
-	In the right automaton, \nmm{\OT{1S}{0S}{\act{tick}}{\mbrc{}}{\top}{\mbrc{}}} has a true guard.
-\end{itemize}
-The left automaton indeed fails at being the result of a non-locking composition where the right automaton passes.
-
-One more thing worth noting is that for the left automaton, in the state \(1C\) with a valuation such that \(t < 0\), the counter agent is in a deadlock state.
-We could have defined the non-locking composition so that this is considered as an intended deadlock, making the requirement symmetric.
-However the the semantics of composition in a hole is asymmetric and the considered specification -as in the deadlock reduction- is the parent automaton.
-\end{exi}
-
-\section{Proof of equivalent definitions}
-
-\subsection{Proof of Lemma \ref{lem:dred}}\label{apx:lemdred}
 Let \(R\) be a pre-simulation between \(A_1 \defobject \OA{S_1}{s_{01}}{V_1}{\sigma_{01}}{J_1}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{V_2}{\sigma_{02}}{J_2}{T_2}\).
@@
 \end{proof}
-
-\subsection{Proof of Lemma \ref{lem:nlced}}\label{apx:lemnlced}
+Unfortunately, in the general case, this property is conflicting with the properties about the relation on automata because every property involving composition would be applicable on composition introducing deadlocks.
+
+\subsection{Issue with deadlock reduction and composition}
+A way to solve the conflict between deadlock reduction and the properties involving composition is to only consider a composition that do not introduce deadlocks.
+With this new condition on validity of composition we are able to define in the next sections a refinement relation where most of the properties of interest are satisfied.
+
+Before characterising a composition which does not introduce deadlocks we need to be able to tell which states are reachable because some deadlocks are not reachable and should not be considered as being introduced.
+\begin{defi}[Reachability]
+For any open automata \(A \defobject \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is a predicate on states satisfying both
+\defitem Inital state is reachable: \(\sigma_0 \vdash \reach{A}\mpar{s_0}\)
+\defitem Reachability is preserved across transitions: \nmm{\forall t \defobject \OTg \in T, \fvars{t} \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}}
+\end{defi}
+The reachability predicate is used to characterise the reachable configurations in a run of an automaton.
+In fact the role of the predicate is to characterise potentially reachable configurations without having to characterise configurations as the result of a valid path in an automaton.
+
+To do that we impose that the initial configuration is reachable and that reachability is preserved by taking valid transitions.
+This effectively makes reachability take into account all paths, and potentially over-approximate the reachable configurations.
+The exact reachability may not be representable in the formulas, hence the need of potentially over-approximating.
+\begin{defi}[Non-locking composition, intuitive definition]
+Let \(A_i \defobject \OAg[i], 0 \leq i \leq n\).
+The composition \(A \defobject A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is non-locking if \(A\) has a reachability predicate satisfying:
+From reachable configurations, if there was a possible transition in \(A_0\) then there is a possible transition in \(A\).
+Formally for \(\OAg \defobject A\), it gives
+\begin{multline*}
+	\forall s \defobject \mpar{s'_i}_{0 \leq i \leq n} \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A}\mpar{s}} \implies \\
+	\mpar{\exists t_0 \in \fOT{s'_0}, \exists \nu_0: \fvars{t_0} \to \values, \sigma \uplus \nu_0 \vdash \fguard{t_0}} \implies \\
+	\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t}
+\end{multline*}
+\end{defi}
+As in the previous section, the definition can be simplified into a less intuitive version:
+\begin{defi}[Non-locking composition, working definition]
+\(A \defobject A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is a non-locking composition if:
+\[ \forall s \defobject \mpar{s_0, s'} \in S, V \uplus \biguplus_\subbox{t_0 \in \fOT{s_0}} \fvars{t_0} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_0 \in \fOT{s_0}} \fguard{t_0} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
+\end{defi}
+\begin{lem} The intuitive and working definition of non-locking composition are equivalent. \end{lem}
 We want to prove
@@
 \end{proof}
-
-\section{Proofs of properties for hole-\(\triangle\) simulation}
-
-\subsection{Hole-\(\triangle\) simulation is a pre-simulation}\label{apx:presim}
+\begin{exi}[Deadlocks introduced by composition]
+This example reuses the counter introduced in Figure \ref{fig:tlh}.
+The behaviour of the counter is to count external \(\act{tick}\) actions up to the amount set by action \(\act{set}\mpar{x}\) then to notify the environment that this amount of time elapsed.
+In the traffic light example the clock is not specified, we will introduce deadlocks using a wisely chosen clock specification.
+However the full traffic light will not be used in order to simplify the example, only the counter will be.
+\begin{figure}
+\input{randomtick_clock.tex}
+\vrule
+\input{register_anytick.tex}
+\caption{On the left: A clock which imposes a tick; On the right: A modified version of the counter at figure \ref{fig:tlh}}
+\label{fig:anytick}
+\end{figure}
+The clock on the left side of Figure \ref{fig:anytick} transmits the actions of its hole unchanged until the clock imposes a \(\act{tick}\) on its hole.
+This can model a physical clock, because physical time ticks cannot be delayed.
+
+If the hole cannot handle a \(\act{tick}\) at any time then there is a deadlock, which is the case with our counter.
+The composition of this clock with the counter is given on the left of Figure \ref{fig:deadlock}.
+\begin{figure}
+\input{Composition_deadlock.tex}
+\vrule
+\input{Composition_nolock.tex}
+\caption{On the left: Deadlocks introduced by composition; On the right: No deadlock introduced by composition}
+\label{fig:deadlock}
+\end{figure}
+There are two deadlocks:
+The first is in the state \(1S\), which corresponds to the clock trying to impose a tick when the counter is not set.
+The second is in the state \(1C\), which corresponds to the clock trying to impose a tick when the counter has reached the amount previously set, but not has not yet reported it to the environment.
+These deadlocks could have been in the specification in which case they were intended, but it is not the case here.
+
+The counter on the right of Figure \ref{fig:anytick} is a modification to accept ticks at in any state.
+Composing this modified counter gives the automaton on the right of Figure \ref{fig:deadlock} which has no deadlocks.
+
+We should successfully characterise the second composition as non-locking but fail for the first.
+\begin{itemize}
+\item In the state \(0S\) any valuation is reachable (no initial valuation).
+	In both automata the transition \nmm{\OT{0S}{1S}{\tau}{\mbrc{}}{\top}{\mbrc{}}} has a true guard, hence the first branch of the disjunction holds.
+\item In the state \(0C\), for the left automaton, valuations where \(t \geq c \geq 0 \vee \mpar{t < 0 \wedge c = 0}\) are reachable; for the right automaton, valuations where \(c \geq 0\) are reachable.
+	For all these valuations the transition \nmm{\OT{0C}{1C}{\tau}{\mbrc{}}{\top}{\mbrc{}}} has a true guard, hence the first branch of the disjunction holds.
+\item In the state \(1C\), the same valuations as the ones reachable in \(0C\) are also reachable.
+	In the right automaton the transition \nmm{\OT{1C}{0C}{\act{tick}}{\mbrc{}}{\top}{\mbrc{c \gets c + 1}}} has a true guard.
+	In the left automaton the transition \nmm{\OT{1C}{0C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} covers the cases where \(c < t\).
+	For the other cases (\(c = t \vee t \leq 0 \mbrk{\leq c}\)) there are no transition with a true guard, and in the clock the transition same transition as for the state \(1S\) has a true guard, hence the composition is not non-locking.
+\item In the state \(1S\) any valuation is reachable.
+	In the left automaton, no transition is possible, and in the parent automaton \nmm{\OT{1}{0}{\act{tick}}{\mbrc{H \mapsto \act{tick}}}{\top}{\mbrc{}}} had a true guard, so the composition is not a non-locking composition (we already know it at this point).
+	In the right automaton, \nmm{\OT{1S}{0S}{\act{tick}}{\mbrc{}}{\top}{\mbrc{}}} has a true guard.
+\end{itemize}
+The left automaton indeed fails at being the result of a non-locking composition where the right automaton passes.
+
+One more thing worth noting is that for the left automaton, in the state \(1C\) with a valuation such that \(t < 0\), the counter agent is in a deadlock state.
+We could have defined the non-locking composition so that this is considered as an intended deadlock, making the requirement symmetric.
+However the the semantics of composition in a hole is asymmetric and the considered specification -as in the deadlock reduction- is the parent automaton.
+\end{exi}
+This new definition of composition can replace the standard composition.
+We may think that if the simultaneous composition is non-locking, then for every composition order, each composition step is non-locking.
+Unfortunately it is not true.
+This happens because in an intermediate composition step, a state can become a deadlock, but in a further composition step it would become unreachable.
+% However the opposite way is true: % Would need a proof, non-trivial
+% If there is an order of composition where every composition is non-locking then the last composition is non-locking, last composition resulting in the same automaton as the simultaneous composition.
+% So the condition is better checked after the simultaneous composition or the last individual composition.
+\begin{exi}
+\begin{figure}
+\centering
+\input{file_sync.tex}
+\caption{A made-up protocol for file synchronisation}
+\label{fig:pnls}
+\end{figure}
+The automaton on Figure \ref{fig:pnls} is a sample protocol for file synchronisation.
+The two holes are \(net\) a process to manage network communications, and \(hash\) a process to check files integrity.
+The state \(i\) is the initial state.
+In that state we want to synchronise the files before working, or work on the local version as a fallback.
+If the preferred version is the remote one, we go in state \(d1\) asking the network manager to fetch the latest version, then ask the integrity checker to validate the files.
+If the preferred version is the local one, we go in state \(d2\) asking for the integrity checker to validate the local files, then ask the network manager to push them.
+In fallback we use the local version.
+
+We can plug an inactive process for the network manager and the file integrity checker by composing a deadlock automaton in their holes, but always both at the same time.
+The reason for that is the simultaneous composition is non-locking, but any individual composition is locking because either the state \(d1\) or \(d2\) (depending on the order) is reachable and becomes a deadlock.
+\end{exi}
+From this point and when checking the refinement properties, composition will only refer to non-locking composition.
+
+\section{Refinement relations in restricted cases}\label{sec:prelref}
+With all these properties explained, we can look at some concrete refinement relations.
+The main goal of this section is to explain the different aspects of refinement in restricted cases so that they are not all introduced at once in the real refinement relation.
+In particular if we have a family of open automata \(A_i \defobject \OAg[i]\), \(0 \leq i \leq n\), let \(A \defobject A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\).
+Recall that there is no relation between the holes of \(A\) and \(A_0\) because \(\mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}\) is neither subset nor superset of \(J_0\).
+So looking at restricted cases where holes are related in a specific manner can help understanding the general case.
+Hopefully the intermediate refinement relation introduced can be used as simpler (and less expensive to compute) versions of the real refinement relation in the case the manipulated automata respect some constraints.
+
+We restrict the holes of the related automata so that we can explain the different refinements without their interactions.
+In the following definition, \(\triangle \in \mbrc{\subseteq, =, \supseteq}\).
+\begin{defi}[Hole-\(\triangle\) simulation]
+For two open automata \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\triangle\) simulation of \(A_1\) by \(A_2\) if:
+\item[1)] \(J_1 \triangle J_2\)
+\item[2)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
+\item[3)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)\vspace{-8pt}
+\noindent\begin{multline*}
+	\mpar{\everymath{\displaystyle}\begin{array}{l}
+		\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
+		\quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
+		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
+			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}}
+	\end{array}} \\
+	\wedge \mpar{V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
+\end{multline*}
+\end{defi}
+The third item of the definition has two parts:
+The first part is the main requirement, a stronger version of the pre-simulation requirement so that it better fits SMT.
+Instead of matching an instanciated transition to another instanciated transition as in the pre-simulation definition, we match an open transition to a family of covering open-transitions.
+The second part is directly the deadlock reduction requirement.
+
+The hole-equal simulation is applicable when the related automata have the same holes.
+It is designed to capture all the refinements other than composition: Duplicating and merging states and transitions, changing variables, removing transitions, adding requirements to guards, specifying more initial variables, and many more.
+
+The hole-subset simulation is applicable when the simulated automaton has less holes.
+It is designed to have composition correctness when the composed automata have no holes.
+
+The hole-superset simulation is applicable when the simulated automaton has more holes.
+It is designed to capture the addition of holes involved in transitions, which will indirectly add requirements to transitions when the new holes will be composed.
+It is also an attempt at giving a meaning to the new holes when composing with any open automata.
+However it does not capture the removal of holes because other issues arise when trying to both add and remove holes.
+\begin{exi}[Example of hole-equal simulation]
+\begin{figure}
+\centering
+\input{parallel_comp.tex}
+\vrule
+\input{n_control_switch.tex}
+\caption{On the left: Parallel composition operator; On the right: n control switches automaton}
+\label{fig:hisim}
+\end{figure}
+Figure \ref{fig:hisim} introduces two related open automata with same holes \(\mbrc{l, r}\).
+The automaton on the left is a parallel composition: any hole can perform actions at any time, the actions are passed unmodified and no synchronisation is performed.
+The automaton on the right is a sequential composition with \(n\) control switches: a hole performs a sequence of actions then the other does, there are \(n\) sequences of a single automaton doing actions without the other performing some.
+
+Intuitively the right automaton is a refinement of the left automaton because the left automaton is what happens when there was no bound \(n\) in the right automaton.
+\[ R \defobject \mbrc{\mpar{l, ||} \mapsto \top, \mpar{r, ||} \mapsto \top} \]
+\(R\) is a hole-identical simulation of \(n\) control switches by parallel composition.
+There are enough examples of proofs of refinement in this report for the reader to be able to prove it as an exercise.
+\end{exi}
+\begin{exi}[Example of hole-subset simulation]
+The automata of Example \ref{exi:full_comp} can be reused here.
+The automaton on Figure \ref{fig:tlf} is a refinement of the one on Figure \ref{fig:tls} by limited composition correctness (Proposition \ref{prop:cc'} below).
+
+It is a simplified version of the motivation for making a refinement relation, which is the traffic light system in an article about weak-bisimulation \cite{wang:03126313}.
+It had to be modified because here the simulation is a strong-simulation (no silent actions).
+\end{exi}
+\begin{exi}[Example of hole-superset simulation]
+\begin{figure}
+\centering
+\input{Vending_machine.tex}
+\vspace{3pt}
+\hrule
+\vspace{3pt}
+\input{Open_vending_machine.tex}
+\caption{On the top: Vending machine; On the bottom: Open vending machine}
+\label{fig:ovm}
+\end{figure}
+Figure \ref{fig:ovm} introduces two related open automata with same states and transitions except for hole actions.
+Both automata are vending machine: Money is introduced while in state \(I\), accumulating in the money variable \(m\), when there are enough money a coffee or a tea can be ordered by taking the transitions to the states \(C\) or \(T\) and money is decreased, then the drink is served by taking the transition back to state \(I\).
+The holes added in the open version on the bottom are \(mon\) a hole which task is to verify the money inserted (coin vary depending on the country for instance) and \(serv\) which task is to serve the drink and report the exact amount served.
+
+The automaton on the bottom is a refinement of the automaton on the top using hole-superset simulation.
+The relation on states is the same as the one for reflexivity.
+Intuitively the automaton on the bottom binds some variables to action produced by the holes, the automaton is no more free to take a transition some hole is not able to perform.
+For instance if the automaton in the hole \(mon\) can only perform \(\act{credit}\mpar{100}\) then after the composition, the automaton on the bottom should be a refinement of the one on the top.
+Actually after such a composition it is still in hole-superset simulation with the top automaton by Proposition \ref{prop:cc'}.
+\end{exi}
+\begin{thm} A hole-\(\triangle\) simulation is a pre-simulation. \end{thm}
 Let \(R\) be a relation on configurations.
@@
 \end{proof}
-
-\subsection{Limited composition correctness for hole-subset simulation}\label{apx:lchs}
-Let \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\) be open automata, where \(J_2 = \emptyset\).
-Let \(k \in J_1\) and \(A \defobject A_1\subst{A_2}{k}\), with \(\OAg \defobject A\).
-Let \(\reach{A}\) be a witness that the composition producing \(A\) is non-locking.
-\[ R \defobject \mpar{\mpar{s_{1'}, s_2}, s_1} \mapsto \choice{\reach{A}\mpar{s_{1'}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1 & \text{if } s_{1'} = s_1 \\ \bot & \text{otherwise}} \]
-Where \(y_1 \mapsto y_{1'}\) is the renaming for \(y\) a variable or a valuation of \(A_1\) in \(A\).
-We want to prove that \(R\) is a hole-subset simulation of \(A\) by \(A_1\).
-\begin{proof}
-\item[1)] \(J = J_2 \uplus J_1 \setminus \mbrc{k} = \emptyset \uplus J_1 \setminus \mbrc{k} \subseteq J_1\)
-\item[2)] We use the fact that \(R\) doesn't constrain the behaviour of \(J_2\) and initial configuration is reachable:
-	\begin{align*}
-		\sigma_0 \uplus \sigma_{01} \vdash R\mpar{s_0, s_{01}} \iff & \mpar{\reach{A}\mpar{s_0} \wedge \bigwedge_{v_1 \in V_1} v_{1'} = v_1}\psubst{\sigma_{01'} \uplus \sigma_{02} \uplus \sigma_{01}} \\
-		\iff & \reach{A}\mpar{s_0}\psubst{\sigma_0} \wedge \bigwedge_\subbox{v_1 \in V_1} \sigma_{01'}\mpar{v_{1'}} = \sigma_{01}\mpar{v_1} \\
-		\iff & \sigma_0 \vdash \reach{A}\mpar{s_0}
-	\end{align*}
-\item[3)] Let \(s \defobject \mpar{s_{1'}, s_2} \in S\) and \(s_1 \in S_1\).
-	We want to prove both
-	\begin{align*}
-		& \bigsymb{\forall} t \defobject \OTg \in \fOT{s}, \bigsymb{\exists} \mpar{t_{1x} \defobject \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X}, \\
-		& \quad \mpar{\forall x \in X, J'_{1x} \cap J = J' \cap J_1} \\[-10pt]
-		& \nwedge V \uplus V_1 \uplus \fvars{t} \vdash R\mpar{s, s_1} \wedge g \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha = \alpha_{1x} \wedge \bigwedge_\subbox{j \in J'_{1x} \cap J} \beta_j = \beta_{1xj} \\[12pt]
-			\nwedge g_{1x} \wedge R\mpar{s', s'_{1x}}\psubst{\psi \uplus \psi_{1x}}
-		\end{array}} \goal{0}
-	\end{align*}
-	\[ V \uplus V_1 \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash R\mpar{s, s_1} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \goal{1} \]
-	Let \nmm{t \defobject \OTg \in \fOT{s}}, we know that \(t\) is obtained by composition so there is a generating transition \(t_1 \in \fOT{s_1}\) for which we will prove \goal{0}.
-	If \(s_{1'} \neq s_1\) we instead prove \goal{0} with the empty family.
-	\begin{gather}
-		\forall x \in X, J'_1 \cap J = J' \cap J_1 \goal{0'} \\
-		V \uplus V_1 \uplus \fvars{t} \vdash R\mpar{s, s_1} \wedge g \implies \alpha = \alpha_1 \wedge \bigwedge_\subbox{j \in J'_1 \cap J} \beta_j = \beta_{1j} \wedge g_1 \wedge R\mpar{s', s'_1}\psubst{\psi \uplus \psi_1} \goal{2}
-	\end{gather}
-\item[\goal{0'}:] \(t\) is a transition built from \(t_1\) so it has its holes.
-	Additionally either \(k \notin J'_1\) so \(J' = J'_1\) or \(k \in J'_1\) so \(J' = \emptyset \uplus J'_1 \setminus \mbrc{k}\) because \(A_2\) has no holes.
-	Either case \(J'_1 \cap J = J'_1 \setminus \mbrc{k} = \mpar{J'_1 \setminus \mbrc{k}} \cap J_1 = J' \cap J_1\).
-\item[\goal{2}:] Let \(\sigma: V \uplus V_1 \uplus \fvars{t} \to \values\).
-	We rename some variables in the domain of definition of \(\sigma\) to get \(\nu: \fvars{t_1} \to \values\).
-	We use \(\nu\) to prove \goal{2}, get the left side of the implication as an hypothesis and break the right side of the implication:
-	\begin{gather}
-		\sigma \vdash R\mpar{s, s_1} \wedge g \hyp{1} \\
-		\sigma \uplus \nu \vdash \alpha = \alpha_1 \goal{2a} \\
-		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_1 \cap J} \beta_j = \beta_{1j} \goal{2b} \\
-		\sigma \uplus \nu \vdash g_1 \goal{2c} \\
-		\sigma \uplus \nu \vdash R\mpar{s', s'_1}\psubst{\psi \uplus \psi_1} \goal{2d}
-	\end{gather}
-	If \(s_{1'} \neq s_1\) then \hyp{1} is \(\sigma \vdash \bot\) so the proof is finished and the empty family worked.
-	Otherwise we can assume \(s_{1'} = s_1\) and break \hyp{1} into
-	\begin{gather}
-		\sigma \vdash \reach{A}\mpar{s} \hyp{1a} \\
-		\sigma \vdash \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1 \hyp{1b} \\
-		\sigma \vdash g \hyp{1c}
-	\end{gather}
-	\goal{2a} holds because composition doesn't change the produced action and the valuation coincide on the renamed variables.
-	\goal{2b} also holds because \(J'_1 \cap J = J'_1 \setminus \mbrc{k} = J'\), composition doesn't change the actions of the holes involved and the valuation coincide on the renamed variables.
-	\goal{2c} is proved using \hyp{1c} (\(g \iff g_1\) or \(g \iff g_1 \wedge \dots\)).
-	For \goal{2d} we use \hyp{1a} with the preservation of reachability across transitions, \hyp{1b} and the fact that the valuations coincide on the renamed values:
-	\begin{align*}
-		& \sigma \uplus \nu \vdash R\mpar{s', s'_1}\psubst{\psi \uplus \psi_1} \\
-		\iff & \sigma \uplus \nu \vdash \mpar{\reach{A}\mpar{s} \wedge \bigwedge_{v_1 \in V_1} v_{1'} = v_1}\psubst{\psi \uplus \psi_1} \\
-		\iff & \sigma \uplus \nu \vdash \reach{A}\mpar{s}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1} \psi_{1'}\mpar{v_{1'}} = \psi_1\mpar{v_1} \\
-		\impliedby & \sigma \uplus \nu \vdash \reach{A}\mpar{s}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1 \uplus \fvars{t_1}} v_{1'} = v_1 \\
-		\iff & \mpar{\sigma \vdash \reach{A}\mpar{s}\psubst{\psi}} \wedge \mpar{\sigma \uplus \nu \vdash \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1}
-	\end{align*}
-\item[\goal{1}:] Let \nmm{\sigma: V \uplus V_1 \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
-	We use dummy values for the variables in \nmm{\biguplus_\subbox{t \in \fOT{s}} \fvars{t}} to get the left side of the implication (independent from these values), immediately broken into
-	\begin{gather}
-		\sigma \vdash \reach{A}\mpar{s} \hyp{2a} \\
-		\sigma \vdash \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1 \hyp{2b} \\
-		\sigma \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{2c}
-	\end{gather}
-	\(\reach{A}\) is a witness of the non-locking composition so we have the hypothesis:
-	\[ V \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{3} \]
-	We use \hyp{3} with valuation \(\sigma\) to get \nmm{\nu: \biguplus_\subbox{t \in \fOT{s}} \fvars{t} \to \values}.
-	The left side of the implication is proved with \hyp{2a} and \hyp{2c}, the right side gives the hypothesis:
-	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{3'} \]
-	We prove \goal{1} with valuation \(\nu\) by admitting the left side of the implication and using \hyp{3'}.
-\end{proof}
-
-\subsection{Special composition correctness for hole-superset simulation}\label{apx:schs}
-Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) be open automata.
-Let \(k \in J_1 \setminus J_2\) and \(A \defobject A_1\subst{A_3}{k}\), with \(\OAg \defobject A\).
-Let \(R_{12}\) be a hole-superset simulation of \(A_1\) by \(A_2\) and \(\reach{A}\) be a witness that the composition producing \(A\) is non-locking.
-\[ R \defobject \mpar{\mpar{s_1, s_3}, s_2} \mapsto R_{12}\mpar{s_1, s_2} \wedge \reach{A}\mpar{s_1, s_3} \]
-We want to prove that \(R\) is a hole-superset simulation of \(A\) by \(A_2\).
-\begin{proof}
-\item[1)] \(J = J_3 \uplus J_1 \setminus \mbrc{k} \supseteq J_3 \uplus J_2 \setminus \mbrc{k} \supseteq J_2 \setminus \mbrc{k} = J_2\)
-\item[2)] We use the fact that \(R_{12}\) relates initial configurations and that initial configuration is reachable:
-	\begin{align*}
-		\sigma_0 \uplus \sigma_{02} \vdash R\mpar{s_0, s_{02}} \iff & \sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03} \vdash R_{12}\mpar{s_{01}, s_{02}} \wedge \reach{A}\mpar{s_0} \\
-		\iff & \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar{\sigma_0 \vdash \reach{A}\mpar{s_0}}
-	\end{align*}
-\item[3)] Let \(s \defobject \mpar{s_1, s_3} \in S\) and \(s_2 \in S_2\).
-	We want to prove both
-	\begin{align*}
-		& \bigsymb{\forall} t \defobject \OTg \in \fOT{s}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
-		& \quad \mpar{\forall x \in X, J'_{2x} \cap J = J' \cap J_2} \\[-10pt]
-		& \nwedge V \uplus V_2 \uplus \fvars{t} \vdash R\mpar{s, s_2} \wedge g \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J} \beta_j = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R\mpar{s', s'_{2x}}\psubst{\psi \uplus \psi_{2x}}
-		\end{array}} \goal{0}
-	\end{align*}
-	\[ V \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \goal{1} \]
-	Let \nmm{t \defobject \OTg \in \fOT{s}}, we use the fact that \(R_{12}\) is a simulation from the states \(\mpar{s_1, s_2}\) to get the hypothesis:
-	\begin{align*}
-		& \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
-		& \quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
-		& \nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R_{12}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}} \hyp{1}
-	\end{align*}
-	Transition \(t\) is obtained by composition of \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}} and \nmm{t_3 \defobject \OTx{3}{}{3}{3} \in \fOT{s_3}} if \(k \in J'_1\) or by a the first transition and the state \(s_3\) if \(k \notin J'_1\).
-	We use \hyp{1} with the transition \(t_1\) to get
-	\begin{gather*}
-		\mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X} \\
-		\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2 \hyp{1'} \\
-		V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R_{12}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}} \hyp{1"}
-	\end{gather*}
-	We will prove \goal{0} for the family \(t_{2x}\), the new goals are
-	\begin{gather}
-		\forall x \in X, J'_{2x} \cap J = J' \cap J_2 \goal{0'} \\
-		V \uplus V_2 \uplus \fvars{t} \vdash R\mpar{s, s_2} \wedge g \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J} \beta_j = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R\mpar{s', s'_{2x}}\psubst{\psi \uplus \psi_{2x}}
-		\end{array}} \goal{2}
-	\end{gather}
-\item[\goal{0'}:] Let \(x \in X\)
-	\begin{align*}
-		J'_{2x} \cap J & = J'_{2x} \cap \mpar{J_3 \uplus J_1 \setminus \mbrc{k}} \\
-		& = J'_{2x} \cap J_1 & \text{by } k \in J_1 \setminus J_2 \text{ and } \emptyset = J_3 \cap J_1 \supseteq J_3 \cap J_2 \hyp{2} \\
-		& = J'_1 \cap J_2 & \text{by \hyp{1'}} \\
-		& = \mpar{J'_1 \uplus J'_3} \cap J_2 \\
-		& = J' \cap J_2
-	\end{align*}
-\item[\goal{2}:] Let \nmm{\sigma: V \uplus V_2 \uplus \fvars{t} \to \values}.
-	We use dummy values for the variables in \nmm{\biguplus_\subbox{t_{2x} \in \fOT{s_2}} \fvars{t_{2x}}} to get the left side of the implication (independent from these values), immediately broken into
-	\begin{gather}
-		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{3a} \\
-		\sigma \vdash \reach{A}\mpar{s} \hyp{3b} \\
-		\sigma \vdash g \hyp{3c}
-	\end{gather}
-	We use \hyp{1"} with valuation \(\sigma\) on variables \(V_1 \uplus V_2 \uplus \fvars{t_1}\), which is possible because the composition of transitions doesn't remove any variable.
-	Then we get the values of the implicit \(\exists\) in \nmm{\nu: \biguplus_{x \in X} \fvars{t_{2x}}}.
-	The left side of the implication is proved with \hyp{3a} and \hyp{3c}.
-	So we get a \(x \in X\) such that
-	\begin{gather}
-		\sigma \uplus \nu \vdash \alpha_1 = \alpha_{2x} \hyp{4a} \\
-		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \hyp{4b} \\
-		\sigma \uplus \nu \vdash g_{2x} \hyp{4c} \\
-		\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \hyp{4d}
-	\end{gather}
-	In order to progress on \goal{2} we give valuation \(\nu\) for the implicit \(\exists\), admit the left side of the implication and choose to prove the branch \(x\):
-	\begin{gather}
-		\sigma \uplus \nu \vdash \alpha = \alpha_{2x} \goal{2a} \\
-		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_{2x} \cap J} \beta_j = \beta_{2xj} \goal{2b} \\
-		\sigma \uplus \nu \vdash g_{2x} \goal{2c} \\
-		\sigma \uplus \nu \vdash R\mpar{s', s'_{2x}}\psubst{\psi \uplus \psi_{2x}} \goal{2d}
-	\end{gather}
-	\goal{2a} is proved by \hyp{4a} (\(\alpha = \alpha_1\)).
-	\goal{2b} is proved using \hyp{4b} because \(J'_{2x} \cap J = J'_{2x} \cap J_1 = J'_1 \cap J_2\) (\hyp{2} and \hyp{1'}) and \(\forall j \in J'_1, \beta_{1j} = \beta_j\) (transition comes from composition).
-	\goal{2c} is proved by \hyp{4c}.
-	For \goal{2d} we use \hyp{4d} and \hyp{3b} with the preservation of reachability across transitions:
-	\begin{align*}
-		& \sigma \uplus \nu \vdash R\mpar{s', s'_{2x}}\psubst{\psi \uplus \psi_{2x}} \\
-		\iff & \sigma \uplus \nu \vdash \mpar{R_{12}\mpar{s'_1, s'_{2x}} \wedge \reach{A}\mpar{s}}\psubst{\psi_1 \uplus \psi_{2x} \uplus \psi_3} \\
-		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \reach{A}\mpar{s}\psubst{\psi}}
-	\end{align*}
-\item[\goal{1}:]
-	Let \nmm{\sigma: V \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values}.
-	We use dummy values for the variables in \nmm{\biguplus_\subbox{t \in \fOT{s}} \fvars{t}} to get the left side of the implication (independent from these values), immediately broken into
-	\begin{gather}
-		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{5a} \\
-		\sigma \vdash \reach{A}\mpar{s} \hyp{5b} \\
-		\sigma \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{5c}
-	\end{gather}
-	\(R_{12}\) is a simulation and \(\reach{A}\) is a witness of the non-locking composition so we have the hypotheses:
-	\begin{gather}
-		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6} \\
-		V \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{7}
-	\end{gather}
-	We use \hyp{6} with valuation \(\sigma\) to get \nmm{\nu: \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
-	The left side of the implication is proved with \hyp{5a} and \hyp{5c}, the right side gives the hypothesis:
-	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{6'} \]
-	We then use \hyp{7} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t \in \fOT{s}} \fvars{t}}.
-	The left side of the implication is proved using \hyp{5b} and \hyp{6'}, the right side gives:
-	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{7'} \]
-	We prove \goal{1} with valuation \(\nu'\) by admitting the left side of the implication and using \hyp{7'}.
-\end{proof}
-
-\section{Proof of transitivity}\label{apx:trans}
+\begin{thm} The hole-\(\triangle\) simulation on automata is a preorder. \end{thm}
+\begin{proofsketch}
+The idea for reflexivity is that the related automata are always in the same configuration.
+\[ R \defobject \mpar{s, s'} \mapsto \choice{\bigwedge_{v \in V} v_1 = v_2 & \text{if } s = s'\\ \bot & \text{otherwise}} \]
+Where \(v_x\) is the renaming to distinguish conflicting automaton variables.
+\(R\) is a witness of the reflexivity, the proof is mainly the same as several of the following ones so it will be omitted.
+\end{proofsketch}
+For transitivity we need to introduce three open automata.
 Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) be open automata.
 Let \(R_{12}\) be a hole-\(\triangle\) simulation of \(A_1\) by \(A_2\) and \(R_{23}\) of \(A_2\) by \(A_3\).
+The idea for \(R\) is that there exists a state \(s_2 \in S_2\) and values for \(V_2\) such that \(R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}\).
+However we cannot talk about states in formulas.
+The solution is to expand the existential quantifier on states as we did in deadlock reduction, which is possible because states are finite.
 \[ R \defobject \mpar{s_1, s_3} \mapsto \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \]
@@
 \end{proof}
-
-\section{Proof or properties for open automata refinement}
-
-\subsection{Context refinement}\label{apx:cr}
-Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) be open automata and \(\mpar{R_{12}, H_{12}}\) be a hole-tracking simulation of \(A_1\) by \(A_2\).
-Let \(k \in H_{12}\), \(A_{13} \defobject A_1\subst{A_3}{k}\), \(A_{23} \defobject A_2\subst{A_3}{k}\) and \(\reach{A_{13}}\) be a witness that the composition producing \(A_{13}\) is non-locking.
+\begin{prop}[Limited composition correctness]\label{prop:cc'}
+Hole-subset simulation is correct w.r.t.\@ composition with automata without holes.
+\end{prop}
+% TODO: Renaming
+Let \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\) be open automata, where \(J_2 = \emptyset\).
+Let \(k \in J_1\) and \(A \defobject A_1\subst{A_2}{k}\), with \(\OAg \defobject A\).
+Let \(\reach{A}\) be a witness that the composition producing \(A\) is non-locking.
+The idea for the relation on configurations is that the copy of \(A_1\) in \(A\) do the same things as \(A_1\), as if we were trying to prove reflexivity.
+\[ R \defobject \mpar{\mpar{s_{1'}, s_2}, s_1} \mapsto \choice{\reach{A}\mpar{s_{1'}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1 & \text{if } s_{1'} = s_1 \\ \bot & \text{otherwise}} \]
+Where \(y_1 \mapsto y_{1'}\) is the renaming for \(y\) a variable or a valuation of \(A_1\) in \(A\).
+% END TODO
+We want to prove that \(R\) is a hole-subset simulation of \(A\) by \(A_1\).
+\begin{proof}
+\item[1)] \(J = J_2 \uplus J_1 \setminus \mbrc{k} = \emptyset \uplus J_1 \setminus \mbrc{k} \subseteq J_1\)
+\item[2)] We use the fact that \(R\) doesn't constrain the behaviour of \(J_2\) and initial configuration is reachable:
+	\begin{align*}
+		\sigma_0 \uplus \sigma_{01} \vdash R\mpar{s_0, s_{01}} \iff & \mpar{\reach{A}\mpar{s_0} \wedge \bigwedge_{v_1 \in V_1} v_{1'} = v_1}\psubst{\sigma_{01'} \uplus \sigma_{02} \uplus \sigma_{01}} \\
+		\iff & \reach{A}\mpar{s_0}\psubst{\sigma_0} \wedge \bigwedge_\subbox{v_1 \in V_1} \sigma_{01'}\mpar{v_{1'}} = \sigma_{01}\mpar{v_1} \\
+		\iff & \sigma_0 \vdash \reach{A}\mpar{s_0}
+	\end{align*}
+\item[3)] Let \(s \defobject \mpar{s_{1'}, s_2} \in S\) and \(s_1 \in S_1\).
+	We want to prove both
+	\begin{align*}
+		& \bigsymb{\forall} t \defobject \OTg \in \fOT{s}, \bigsymb{\exists} \mpar{t_{1x} \defobject \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X}, \\
+		& \quad \mpar{\forall x \in X, J'_{1x} \cap J = J' \cap J_1} \\[-10pt]
+		& \nwedge V \uplus V_1 \uplus \fvars{t} \vdash R\mpar{s, s_1} \wedge g \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha = \alpha_{1x} \wedge \bigwedge_\subbox{j \in J'_{1x} \cap J} \beta_j = \beta_{1xj} \\[12pt]
+			\nwedge g_{1x} \wedge R\mpar{s', s'_{1x}}\psubst{\psi \uplus \psi_{1x}}
+		\end{array}} \goal{0}
+	\end{align*}
+	\[ V \uplus V_1 \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash R\mpar{s, s_1} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \goal{1} \]
+	Let \nmm{t \defobject \OTg \in \fOT{s}}, we know that \(t\) is obtained by composition so there is a generating transition \(t_1 \in \fOT{s_1}\) for which we will prove \goal{0}.
+	If \(s_{1'} \neq s_1\) we instead prove \goal{0} with the empty family.
+	\begin{gather}
+		\forall x \in X, J'_1 \cap J = J' \cap J_1 \goal{0'} \\
+		V \uplus V_1 \uplus \fvars{t} \vdash R\mpar{s, s_1} \wedge g \implies \alpha = \alpha_1 \wedge \bigwedge_\subbox{j \in J'_1 \cap J} \beta_j = \beta_{1j} \wedge g_1 \wedge R\mpar{s', s'_1}\psubst{\psi \uplus \psi_1} \goal{2}
+	\end{gather}
+\item[\goal{0'}:] \(t\) is a transition built from \(t_1\) so it has its holes.
+	Additionally either \(k \notin J'_1\) so \(J' = J'_1\) or \(k \in J'_1\) so \(J' = \emptyset \uplus J'_1 \setminus \mbrc{k}\) because \(A_2\) has no holes.
+	Either case \(J'_1 \cap J = J'_1 \setminus \mbrc{k} = \mpar{J'_1 \setminus \mbrc{k}} \cap J_1 = J' \cap J_1\).
+\item[\goal{2}:] Let \(\sigma: V \uplus V_1 \uplus \fvars{t} \to \values\).
+	We rename some variables in the domain of definition of \(\sigma\) to get \(\nu: \fvars{t_1} \to \values\).
+	We use \(\nu\) to prove \goal{2}, get the left side of the implication as an hypothesis and break the right side of the implication:
+	\begin{gather}
+		\sigma \vdash R\mpar{s, s_1} \wedge g \hyp{1} \\
+		\sigma \uplus \nu \vdash \alpha = \alpha_1 \goal{2a} \\
+		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_1 \cap J} \beta_j = \beta_{1j} \goal{2b} \\
+		\sigma \uplus \nu \vdash g_1 \goal{2c} \\
+		\sigma \uplus \nu \vdash R\mpar{s', s'_1}\psubst{\psi \uplus \psi_1} \goal{2d}
+	\end{gather}
+	If \(s_{1'} \neq s_1\) then \hyp{1} is \(\sigma \vdash \bot\) so the proof is finished and the empty family worked.
+	Otherwise we can assume \(s_{1'} = s_1\) and break \hyp{1} into
+	\begin{gather}
+		\sigma \vdash \reach{A}\mpar{s} \hyp{1a} \\
+		\sigma \vdash \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1 \hyp{1b} \\
+		\sigma \vdash g \hyp{1c}
+	\end{gather}
+	\goal{2a} holds because composition doesn't change the produced action and the valuation coincide on the renamed variables.
+	\goal{2b} also holds because \(J'_1 \cap J = J'_1 \setminus \mbrc{k} = J'\), composition doesn't change the actions of the holes involved and the valuation coincide on the renamed variables.
+	\goal{2c} is proved using \hyp{1c} (\(g \iff g_1\) or \(g \iff g_1 \wedge \dots\)).
+	For \goal{2d} we use \hyp{1a} with the preservation of reachability across transitions, \hyp{1b} and the fact that the valuations coincide on the renamed values:
+	\begin{align*}
+		& \sigma \uplus \nu \vdash R\mpar{s', s'_1}\psubst{\psi \uplus \psi_1} \\
+		\iff & \sigma \uplus \nu \vdash \mpar{\reach{A}\mpar{s} \wedge \bigwedge_{v_1 \in V_1} v_{1'} = v_1}\psubst{\psi \uplus \psi_1} \\
+		\iff & \sigma \uplus \nu \vdash \reach{A}\mpar{s}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1} \psi_{1'}\mpar{v_{1'}} = \psi_1\mpar{v_1} \\
+		\impliedby & \sigma \uplus \nu \vdash \reach{A}\mpar{s}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1 \uplus \fvars{t_1}} v_{1'} = v_1 \\
+		\iff & \mpar{\sigma \vdash \reach{A}\mpar{s}\psubst{\psi}} \wedge \mpar{\sigma \uplus \nu \vdash \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1}
+	\end{align*}
+\item[\goal{1}:] Let \nmm{\sigma: V \uplus V_1 \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
+	We use dummy values for the variables in \nmm{\biguplus_\subbox{t \in \fOT{s}} \fvars{t}} to get the left side of the implication (independent from these values), immediately broken into
+	\begin{gather}
+		\sigma \vdash \reach{A}\mpar{s} \hyp{2a} \\
+		\sigma \vdash \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1 \hyp{2b} \\
+		\sigma \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{2c}
+	\end{gather}
+	\(\reach{A}\) is a witness of the non-locking composition so we have the hypothesis:
+	\[ V \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{3} \]
+	We use \hyp{3} with valuation \(\sigma\) to get \nmm{\nu: \biguplus_\subbox{t \in \fOT{s}} \fvars{t} \to \values}.
+	The left side of the implication is proved with \hyp{2a} and \hyp{2c}, the right side gives the hypothesis:
+	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{3'} \]
+	We prove \goal{1} with valuation \(\nu\) by admitting the left side of the implication and using \hyp{3'}.
+\end{proof}
+\begin{prop}[Special composition correctness]
+If there is a hole-superset simulation of \(A_1\) by \(A_2\) and \(A_1\subst{A_3}{k}\) is non-locking, then there is a hole-superset simulation of \(A_1\subst{A_3}{k}\) by \(A_2\).
+Where \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\), \(A_3\) are open automata and \(k \in J_1 \setminus J_2\).
+\end{prop}
+% TODO: Renaming
+Let \(\OAg[3] \defobject A_3\) and \(A \defobject A_1\subst{A_3}{k}\), with \(\OAg \defobject A\).
+Let \(R_{12}\) be a hole-superset simulation of \(A_1\) by \(A_2\) and \(\reach{A_1\subst{A_3}{k}}\) be a witness that \(A_1\subst{A_3}{k}\) is non-locking.
+The idea for the relation on configurations is to combine the non-locking composition and the already existing relation on configurations.
+\[ R \defobject \mpar{\mpar{s_1, s_3}, s_2} \mapsto R_{12}\mpar{s_1, s_2} \wedge \reach{A}\mpar{s_1, s_3} \]
+% END TODO
+We want to prove that \(R\) is a hole-superset simulation of \(A\) by \(A_2\).
+\begin{proof}
+\item[1)] \(J = J_3 \uplus J_1 \setminus \mbrc{k} \supseteq J_3 \uplus J_2 \setminus \mbrc{k} \supseteq J_2 \setminus \mbrc{k} = J_2\)
+\item[2)] We use the fact that \(R_{12}\) relates initial configurations and that initial configuration is reachable:
+	\begin{align*}
+		\sigma_0 \uplus \sigma_{02} \vdash R\mpar{s_0, s_{02}} \iff & \sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03} \vdash R_{12}\mpar{s_{01}, s_{02}} \wedge \reach{A}\mpar{s_0} \\
+		\iff & \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar{\sigma_0 \vdash \reach{A}\mpar{s_0}}
+	\end{align*}
+\item[3)] Let \(s \defobject \mpar{s_1, s_3} \in S\) and \(s_2 \in S_2\).
+	We want to prove both
+	\begin{align*}
+		& \bigsymb{\forall} t \defobject \OTg \in \fOT{s}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
+		& \quad \mpar{\forall x \in X, J'_{2x} \cap J = J' \cap J_2} \\[-10pt]
+		& \nwedge V \uplus V_2 \uplus \fvars{t} \vdash R\mpar{s, s_2} \wedge g \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J} \beta_j = \beta_{2xj} \\[12pt]
+			\nwedge g_{2x} \wedge R\mpar{s', s'_{2x}}\psubst{\psi \uplus \psi_{2x}}
+		\end{array}} \goal{0}
+	\end{align*}
+	\[ V \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \goal{1} \]
+	Let \nmm{t \defobject \OTg \in \fOT{s}}, we use the fact that \(R_{12}\) is a simulation from the states \(\mpar{s_1, s_2}\) to get the hypothesis:
+	\begin{align*}
+		& \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
+		& \quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
+		& \nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R_{12}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
+			\nwedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}} \hyp{1}
+	\end{align*}
+	Transition \(t\) is obtained by composition of \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}} and \nmm{t_3 \defobject \OTx{3}{}{3}{3} \in \fOT{s_3}} if \(k \in J'_1\) or by a the first transition and the state \(s_3\) if \(k \notin J'_1\).
+	We use \hyp{1} with the transition \(t_1\) to get
+	\begin{gather*}
+		\mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X} \\
+		\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2 \hyp{1'} \\
+		V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R_{12}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
+			\nwedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}} \hyp{1"}
+	\end{gather*}
+	We will prove \goal{0} for the family \(t_{2x}\), the new goals are
+	\begin{gather}
+		\forall x \in X, J'_{2x} \cap J = J' \cap J_2 \goal{0'} \\
+		V \uplus V_2 \uplus \fvars{t} \vdash R\mpar{s, s_2} \wedge g \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J} \beta_j = \beta_{2xj} \\[12pt]
+			\nwedge g_{2x} \wedge R\mpar{s', s'_{2x}}\psubst{\psi \uplus \psi_{2x}}
+		\end{array}} \goal{2}
+	\end{gather}
+\item[\goal{0'}:] Let \(x \in X\)
+	\begin{align*}
+		J'_{2x} \cap J & = J'_{2x} \cap \mpar{J_3 \uplus J_1 \setminus \mbrc{k}} \\
+		& = J'_{2x} \cap J_1 & \text{by } k \in J_1 \setminus J_2 \text{ and } \emptyset = J_3 \cap J_1 \supseteq J_3 \cap J_2 \hyp{2} \\
+		& = J'_1 \cap J_2 & \text{by \hyp{1'}} \\
+		& = \mpar{J'_1 \uplus J'_3} \cap J_2 \\
+		& = J' \cap J_2
+	\end{align*}
+\item[\goal{2}:] Let \nmm{\sigma: V \uplus V_2 \uplus \fvars{t} \to \values}.
+	We use dummy values for the variables in \nmm{\biguplus_\subbox{t_{2x} \in \fOT{s_2}} \fvars{t_{2x}}} to get the left side of the implication (independent from these values), immediately broken into
+	\begin{gather}
+		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{3a} \\
+		\sigma \vdash \reach{A}\mpar{s} \hyp{3b} \\
+		\sigma \vdash g \hyp{3c}
+	\end{gather}
+	We use \hyp{1"} with valuation \(\sigma\) on variables \(V_1 \uplus V_2 \uplus \fvars{t_1}\), which is possible because the composition of transitions doesn't remove any variable.
+	Then we get the values of the implicit \(\exists\) in \nmm{\nu: \biguplus_{x \in X} \fvars{t_{2x}}}.
+	The left side of the implication is proved with \hyp{3a} and \hyp{3c}.
+	So we get a \(x \in X\) such that
+	\begin{gather}
+		\sigma \uplus \nu \vdash \alpha_1 = \alpha_{2x} \hyp{4a} \\
+		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \hyp{4b} \\
+		\sigma \uplus \nu \vdash g_{2x} \hyp{4c} \\
+		\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \hyp{4d}
+	\end{gather}
+	In order to progress on \goal{2} we give valuation \(\nu\) for the implicit \(\exists\), admit the left side of the implication and choose to prove the branch \(x\):
+	\begin{gather}
+		\sigma \uplus \nu \vdash \alpha = \alpha_{2x} \goal{2a} \\
+		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_{2x} \cap J} \beta_j = \beta_{2xj} \goal{2b} \\
+		\sigma \uplus \nu \vdash g_{2x} \goal{2c} \\
+		\sigma \uplus \nu \vdash R\mpar{s', s'_{2x}}\psubst{\psi \uplus \psi_{2x}} \goal{2d}
+	\end{gather}
+	\goal{2a} is proved by \hyp{4a} (\(\alpha = \alpha_1\)).
+	\goal{2b} is proved using \hyp{4b} because \(J'_{2x} \cap J = J'_{2x} \cap J_1 = J'_1 \cap J_2\) (\hyp{2} and \hyp{1'}) and \(\forall j \in J'_1, \beta_{1j} = \beta_j\) (transition comes from composition).
+	\goal{2c} is proved by \hyp{4c}.
+	For \goal{2d} we use \hyp{4d} and \hyp{3b} with the preservation of reachability across transitions:
+	\begin{align*}
+		& \sigma \uplus \nu \vdash R\mpar{s', s'_{2x}}\psubst{\psi \uplus \psi_{2x}} \\
+		\iff & \sigma \uplus \nu \vdash \mpar{R_{12}\mpar{s'_1, s'_{2x}} \wedge \reach{A}\mpar{s}}\psubst{\psi_1 \uplus \psi_{2x} \uplus \psi_3} \\
+		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \reach{A}\mpar{s}\psubst{\psi}}
+	\end{align*}
+\item[\goal{1}:]
+	Let \nmm{\sigma: V \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values}.
+	We use dummy values for the variables in \nmm{\biguplus_\subbox{t \in \fOT{s}} \fvars{t}} to get the left side of the implication (independent from these values), immediately broken into
+	\begin{gather}
+		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{5a} \\
+		\sigma \vdash \reach{A}\mpar{s} \hyp{5b} \\
+		\sigma \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{5c}
+	\end{gather}
+	\(R_{12}\) is a simulation and \(\reach{A}\) is a witness of the non-locking composition so we have the hypotheses:
+	\begin{gather}
+		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6} \\
+		V \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{7}
+	\end{gather}
+	We use \hyp{6} with valuation \(\sigma\) to get \nmm{\nu: \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
+	The left side of the implication is proved with \hyp{5a} and \hyp{5c}, the right side gives the hypothesis:
+	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{6'} \]
+	We then use \hyp{7} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t \in \fOT{s}} \fvars{t}}.
+	The left side of the implication is proved using \hyp{5b} and \hyp{6'}, the right side gives:
+	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{7'} \]
+	We prove \goal{1} with valuation \(\nu'\) by admitting the left side of the implication and using \hyp{7'}.
+\end{proof}
+The hole-subset simulation can only tell if there is a refinement when the composed automata have no holes.
+To lift this limitation we need to allow adding holes which doesn't have a direct interpretation.
+
+At first a solution using a function mapping the action performed by the new holes in the composition to the ones performed by removed hole in the base automaton was explored.
+It was abandoned because the base automaton has nothing intelligent to tell about the action required by the composed automata.
+That is the reason the hole-superset simulation doesn't constrain the action performed by the added holes.
+The solution adopted is to give a meaning to adding hole and only adding in a simulation.
+With the hole-superset simulation we have an interpretation to added holes:
+They are holes imposing a restriction on the transition variables.
+However with that solution we cannot remove holes so we cannot express composition correctness, hence the need of the special composition correctness for hole-superset simulation.
+
+For composition correctness, using only one of the hole-\(\triangle\) simulations cannot tell that a non-locking composition with any open automaton is a refinement of the base automaton because we need at the same time to add and remove holes.
+If we build the refinement relation as the transitive closure of all the hole-\(\triangle\) simulations then an issue arise.
+The transitivity propriety causes that when a hole present in both extrema of the chain but absent in an intermediate automaton, there is a refinement between the extrema of the chain.
+In that case all the constraint on holes actions are lifted even if we would like to require an equality of these actions on the transitive closure.
+
+\section{Refinement relation for open automata}\label{sec:refinement}
+One solution to solve the issue presented at the end of previous section, that is to keep transitivity and constraints on holes actions from same holes, is to keep track of which holes are in common at each step of refinement.
+The transitive refinement will have to either rename the holes without constraints or explicitly say which holes have constraints.
+\begin{defi}[Open automata refinement]
+For two open automata \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a refinement of \(A_2\) looking at \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), is defined as:
+\begin{multline*}
+	\exists R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2], \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge \forall \mpar{s_1, s_2} \in S_1 \times S_2, \\
+	\mpar{\everymath{\displaystyle}\begin{array}{l}
+		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\[12pt]
+		\quad \mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H} \\[-10pt]
+		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \\
+			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}} \\
+	\end{array}} \\
+	\wedge V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
+\end{multline*}
+Giving \(R\) and \(H\) is sufficient to characterise the refinement, so we call \(\mpar{R, H}\) a hole-tracking simulation of \(A_1\) by \(A_2\).
+Hole in \(H\) are called tracked holes.
+\end{defi}
+\(R\) is a kind of hole-\(\triangle\) simulation but without the \(\triangle\) constraint on hole sets.
+On top of that every action of the holes outside \(H\) is unconstrained in the related automata.
+
+This definition is close to the refinement relation deduced from hole-\(\triangle\) simulations.
+Actually the latter are particular cases of this one.
+Let \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\) be two open automata.
+If \(J_1 = J_2\), we have \(\wrel{A_1}{A_2}{J_1}\) if and only if there is a hole-equal simulation of \(A_1\) by \(A_2\).
+If \(J_1 \subseteq J_2\), we have \(\wrel{A_1}{A_2}{J_1}\) if and only if there is a hole-subset simulation of \(A_1\) by \(A_2\).
+Finally if \(J_1 \supseteq J_2\), we have \(\wrel{A_1}{A_2}{J_2}\) if and only if there is a hole-superset simulation of \(A_1\) by \(A_2\).
+
+The idea behind the set of tracked holes is that a tracked hole is guaranteed to behave well with composition.
+To have guarantees on a hole when performing successive refinement we must keep the hole tracked in every refinement step.
+Otherwise everything happens as if the hole of the most refined automaton is not the same as the one with the same name in the least refined automaton.
+It shouldn't be surprising if at some refinement step all the constraints on a hole are lost, that in the whole process they also are.
+It is the best we can do and if someone want to keep the constraint, then they should choose wisely the intermediate automata used for the refinement.
+
+In terms of transitivity, for the open automata refinement, the strongest property we can prove becomes \(\wrel{A}{B}{X} \wedge \wrel{B}{C}{Y} \implies \wrel{A}{C}{X \cap Y}\).
+For a weaker property we can use the fact that \(\wrel{A_1}{A_2}{H} \implies \wrel{A_1}{A_2}{H'}\) when \(H' \subseteq H\).
+Transitivity behaves the same as if the holes outside the intersection were renamed to avoid conflicts in the first place.
+This in combination with the fact that hole-\(\triangle\) simulation are a particular case of hole-tracking simulation makes the combination of the transitivity proofs of hole-\(\triangle\) simulation sufficient to prove transitivity.
+
+Not renaming conflicting holes still have an interest.
+If we are trying to build an automaton \(A\) with several constraints \(\wrel{A}{A_i}{J_{Ai}}, i \in I\) (as done in B method \cite{cansell:inria-00099794}) and each \(A_i\) is a refinement of some automaton \(C\) then we can have each \(A_i\) constrain a different subset of \(A\)'s holes.
+On each individual path \(A \leq_{J_{Ai}} A_i \leq_{J_{Ai}} C\), some holes of \(A\) are unconstrained but when considering all path they are all constrained.
+However this doesn't implies \(A \leq_{\bigcup_{i \in I} J_{Ai}} C\), it has to be checked separately.
+\begin{exi}
+\begin{figure}
+\centering
+\input{identity.tex}
+\vrule
+\input{any.tex}
+\vrule
+\input{handshake_comp}
+\caption{On the left: Generic identity on holes; On the center: Any action automaton; On the right: Handshake composition.}
+\label{fig:sevpathref}
+\end{figure}
+We have two refinement paths when \(h\) is replaced by \(l\) and by \(r\) in identity on holes (left of Figure \ref{fig:sevpathref}): the parallel composition (left of Figure \ref{fig:hisim}) is a refinement of the identity on holes, which is a refinement of the handshake composition (right of Figure \ref{fig:sevpathref}).
+However we do not have the parallel composition being a refinement of the handshake composition looking at \(\mbrc{l, r}\).
+
+The example also shows a property worth mentioning.
+The holes not tracked are equivalent to having the any action automaton (center of Figure \ref{fig:sevpathref}) composed.
+Actually all the previous refinement are both ways: we can compose the any action automaton in hole \(r\) of the parallel composition to get the other way of the refinement with the identity on holes by composition correctness, and we transform the transition from the identity on holes into the one of the handshake composition by hole-superset refinement.
+\end{exi}
+The other interesting properties left to check are correctness w.r.t.\@ composition, context refinement, composition congruence and compatibility with FH-bisimulation.
+They have to be slightly modified because of the tracked holes set.
+Proving them for the open automata refinement will also prove them for each hole-\(\triangle\) simulation as they are just particular cases.
+\begin{thm}
+Open automata refinement is correct w.r.t.\@ composition.
+The tracked holes are the holes of the base automaton minus the composed hole.
+\end{thm}
+\begin{proof}
+We will decompose composition into two refinement steps, transitivity will complete the proof.
+Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(k \in J_1\) such that \(A_1\subst{A_2}{k}\) is non-locking.
+We pose \(A'_2\) as \(A_2\) stripped of its holes.
+\begin{align*}
+	A'_2 \defobject & \OA{S_2}{s_{02}}{V_2}{\sigma_{02}}{\emptyset}{T'_2} \\
+	T'_2 \defobject & \mset{\OT{s}{s'}{\alpha}{\mbrc{}}{g}{\psi}}{\OTg \in T_2}
+\end{align*}
+By limited composition correctness we have \(\wrel{A_1\subst{A'_2}{k}}{A_1}{J_1 \setminus \mbrc{k}}\).
+Adding holes and binding actions to the new holes is a refinement for hole-superset simulation so we have \(\wrel{A_1\subst{A_2}{k}}{A_1\subst{A'_2}{k}}{J_1 \setminus \mbrc{k}}\).
+By transitivity we have composition correctness.
+\end{proof}
+\begin{thm}[Context refinement]
+Open automata refinement is context refining when the composition happens in a tracked hole:
+Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\).
+Let \(\mpar{R_{12}, H_{12}}\) be a hole-tracking simulation of \(A_1\) by \(A_2\), \(k \in H_{12}\) and \(\reach{A_1\subst{A_3}{k}}\) be a witness that \(A_1\subst{A_3}{k}\) is non-locking.
+Let \(H \defobject J_3 \uplus H_{12} \setminus \mbrc{k}\).
+We have \(\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{H}\).
+\end{thm}
+% TODO: Renaming
+Let \(A_{13} \defobject A_1\subst{A_3}{k}\) and \(A_{23} \defobject A_2\subst{A_3}{k}\).
 We pose \(\OAg[13] \defobject A_{13}\) and \(\OAg[23] \defobject A_{23}\).
-\begin{align*}
-	R \defobject & \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \\
-	H \defobject & J_3 \uplus H_{12} \setminus \mbrc{k}
-\end{align*}
+We have \(\reach{A_{13}} = \reach{A_1\subst{A_3}{k}}\).
+The idea for the relation on configurations is that \(A_2\) simulates \(A_1\) while \(A_3\) does the same things in both compositions in the hole \(k\).
+\[ R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \]
 Where \(y_3 \mapsto y_{3x}\) is the renaming for \(y\) a variable or a valuation of \(A_3\) in \(A_{x3}\).
+% END TODO
 We want to prove that \(\mpar{R, H}\) is a witness of \(\wrel{A_{13}}{A_{23}}{H}\).
@@
 \end{proof}
-
-\subsection{Congruence for composition}\label{apx:cong}
-Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) be three open automata.
+\begin{thm}[Composition congruence]
+Open automata refinement is congruent for composition:
+Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\).
 Let \(k \in J_1\), \(\mpar{R_{23}, H_{23}}\) be a hole-tracking simulation of \(A_2\) by \(A_3\) and \(\reach{A_1\subst{A_2}{k}}\) be a witness that \(A_1\subst{A_2}{k}\) is non-locking.
+Let \(H \defobject H_{23} \uplus J_1 \setminus \mbrc{k}\).
+We have \(\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{H}\).
+\end{thm}
+% TODO: Renaming
 We pose \(\OAg[21] \defobject A_{21}\) and \(\OAg[31] \defobject A_{31}\).
-\begin{align*}
-	R \defobject & \mpar{\mpar{s_{12}, s_2}, \mpar{s_{13}, s_3}} \mapsto \choice{R_{23}\mpar{s_2, s_3} \wedge \reach{A_{21}}\mpar{s_{12}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{12} = v_{13} & \text{if } s_{12} = s_{13} \\ \bot & \text{otherwise}} \\
-	H \defobject & H_{23} \uplus J_1 \setminus \mbrc{k}
-\end{align*}
+The idea for the relation on configurations is that \(A_3\) simulates \(A_2\) while \(A_1\) does the same things in both compositions.
+\[ R \defobject \mpar{\mpar{s_{12}, s_2}, \mpar{s_{13}, s_3}} \mapsto \choice{R_{23}\mpar{s_2, s_3} \wedge \reach{A_{21}}\mpar{s_{12}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{12} = v_{13} & \text{if } s_{12} = s_{13} \\ \bot & \text{otherwise}} \]
 Where \(y_1 \mapsto y_{1x}\) is the renaming for \(y\) a variable or a valuation of \(A_1\) in \(A_{x1}\).
+% END TODO
 We want to prove that \(\mpar{R, H}\) is a witness of \(\wrel{A_{21}}{A_{31}}{H}\).
@@
 \end{proof}
+\begin{thm}[FH-bisimulation compatibility] Open automata refinement is compatible with FH-bisimulation \end{thm}
+\begin{proofsketch} The requirements of FH-bisimulation are strictly stronger than the open automata refinement so using transitivity is sufficient. \end{proofsketch}
+With that last property, every interesting property is proved for the presented refinement relation.
+
+\section{Conclusion}\label{sec:ccl}
+In this report we redefined on open automata an operation from open pNets called composition.
+This operation was defined as the composition of the open pNets used to generate the open automata and not directly on open automata.
+So to reason on composition directly and to better separate the models the definition had to be given without introducing open pNets.
+Then we recalled the main properties expected from a refinement relation on a structure with composition and adapted them to open automata.
+To do that we restricted the composition so that it doesn't introduce deadlocks.
+Then we introduced several refinement relations in restricted cases to avoid dealing immediately with the hard issue of the incomparability of hole sets.
+Finally we introduced a refinement relation having all the interesting properties and dealing with the aforementioned issue at the cost of a slight modification on transitivity.
+
+However the refinement presented here still do not work on the motivating example because of silent actions.
+To be able to refine in the presence of silent action, a weak variant of the simulation is needed.
+This variant will also probably be able to encompass action refinement as a valid refinement because the mechanism are similar.
+
+\pagebreak
+\bibliographystyle{plain}
+\bibliography{biblio}
 

### 2021-06-23 2021-Refinement/report.tex
Test fix for renaming, G3x not finished

@@
 This property is useful if we want to characterise the kind of operations that can generate any refined automaton starting from the specification.
-We won't have it because extending the domain of definition of the initial valuation will be a refinement which can't be expressed with composition.
+We won't have it because extending the definition domain of the initial valuation will be a refinement which can't be expressed with composition.
 Yet a ``completeness w.r.t.\@ some set of operations" is still a strong and interesting property.
@@
 \begin{thm} A hole-\(\triangle\) simulation is a pre-simulation. \end{thm}
+\begin{proof}
 Let \(R\) be a relation on configurations.
@@
 \end{multline}
-\begin{proof} Let \(\mpar{s_1, s_2} \in S_1 \times S_2\), \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}} and \(\sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values\) be such that
+Let \(\mpar{s_1, s_2} \in S_1 \times S_2\), \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}} and \(\sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values\) be such that
 \[ \sigma \vdash R\mpar{s_1, s_2} \wedge g_1 \hyp{1} \]
@@
 	\goal{2c} is exactly \hyp{6c}.
-	We prove \goal{2d} with valuation \(\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}\) for the branch \(s_2\) using \hyp{5d} and \hyp{6d}, more details on why the manipulations are possible are in the proof for transitivity of FH-bisimulation \cite{2007.10770}:
+	We prove \goal{2d} with valuation \(\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}\) for the branch \(s_2\):
 	\begin{align*}
 		& \sigma_1 \uplus \sigma_3 \uplus \nu_3 \vdash R\mpar{s'_1, s'_{3z}}\psubst{\psi_1 \uplus \psi_{3z}} \\
-		\iff & \mpar{R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}}\psubst{\psi_1 \uplus \psi_{3z}}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_1 \uplus \sigma_3 \uplus \nu_3} \\
-		\iff & R_{12}\mpar{s_1, s_2}\psubst{\psi_1}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_1} \wedge R_{23}\mpar{s_2, s_3}\psubst{\psi_{3z}}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_3 \uplus \nu_3} \\
-		\iff & R_{12}\mpar{s_1, s_2}\psubst{\psi_1 \uplus \psi_{s2x}}\psubst{\sigma_2 \uplus \nu_2 \uplus \sigma_1} \wedge R_{23}\mpar{s_2, s_3}\psubst{\psi_{3z} \uplus \psi_{s2x}}\psubst{\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3} \\
-		\iff & \mpar{\sigma_2 \uplus \nu_2 \uplus \sigma_1 \vdash R_{12}\mpar{s_1, s_2}\psubst{\psi_1 \uplus \psi_{s2x}}} \wedge \mpar{\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3 \vdash R_{23}\mpar{s_2, s_3}\psubst{\psi_{3z} \uplus \psi_{s2x}}}
-	\end{align*}
+		\iff & \mpar{R_{12}\mpar{s'_1, s'_2} \wedge R_{23}\mpar{s'_2, s'_3}}\psubst{\psi_1 \uplus \psi_{3z}}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_1 \uplus \sigma_3 \uplus \nu_3} \\
+		\iff & R_{12}\mpar{s'_1, s'_2}\psubst{\psi_1}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_1} \wedge R_{23}\mpar{s'_2, s'_3}\psubst{\psi_{3z}}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_3 \uplus \nu_3} \\
+		\iff & R_{12}\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_{s2x}}\psubst{\sigma_2 \uplus \nu_2 \uplus \sigma_1} \wedge R_{23}\mpar{s'_2, s'_3}\psubst{\psi_{3z} \uplus \psi_{s2x}}\psubst{\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3} \\
+		\iff & \mpar{\sigma_2 \uplus \nu_2 \uplus \sigma_1 \vdash R_{12}\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_{s2x}}} \wedge \mpar{\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3 \vdash R_{23}\mpar{s'_2, s'_3}\psubst{\psi_{3z} \uplus \psi_{s2x}}}
+	\end{align*}
+	Which is proved by \hyp{5d} and \hyp{6d}.
+	The manipulations of substitutions are possible because their definition domain are disjoint; more details are available in the proof for transitivity of FH-bisimulation \cite{2007.10770}.
 \item[\goal{1}:] Let \(\sigma_1: V_1 \to \values\) and \nmm{\sigma_3: V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \to \values}.
@@
 \end{prop}
-% TODO: Renaming
 Let \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\) be open automata, where \(J_2 = \emptyset\).
 Let \(k \in J_1\) and \(A \defobject A_1\subst{A_2}{k}\), with \(\OAg \defobject A\).
-Let \(\reach{A}\) be a witness that the composition producing \(A\) is non-locking.
+Let \(v_1 \mapsto v_{1'}\) be the renaming for \(v_1 \in V_1\) in \(A\).
+Let \(\reach{A}\) be a witness that the composition \(A_1\subst{A_2}{k}\) is non-locking.
 The idea for the relation on configurations is that the copy of \(A_1\) in \(A\) do the same things as \(A_1\), as if we were trying to prove reflexivity.
 \[ R \defobject \mpar{\mpar{s_{1'}, s_2}, s_1} \mapsto \choice{\reach{A}\mpar{s_{1'}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1 & \text{if } s_{1'} = s_1 \\ \bot & \text{otherwise}} \]
-Where \(y_1 \mapsto y_{1'}\) is the renaming for \(y\) a variable or a valuation of \(A_1\) in \(A\).
-% END TODO
 We want to prove that \(R\) is a hole-subset simulation of \(A\) by \(A_1\).
@@
 \item[\goal{2}:] Let \(\sigma: V \uplus V_1 \uplus \fvars{t} \to \values\).
-	We rename some variables in the domain of definition of \(\sigma\) to get \(\nu: \fvars{t_1} \to \values\).
+	We rename some variables in the definition domain of \(\sigma\) to get \(\nu: \fvars{t_1} \to \values\).
 	We use \(\nu\) to prove \goal{2}, get the left side of the implication as an hypothesis and break the right side of the implication:
@@
 	\goal{2c} is proved using \hyp{1c} (\(g \iff g_1\) or \(g \iff g_1 \wedge \dots\)).
-	For \goal{2d} we use \hyp{1a} with the preservation of reachability across transitions, \hyp{1b} and the fact that the valuations coincide on the renamed values:
+	For \goal{2d} we first perform a transformation.
 	\begin{align*}
 		& \sigma \uplus \nu \vdash R\mpar{s', s'_1}\psubst{\psi \uplus \psi_1} \\
-		\iff & \sigma \uplus \nu \vdash \mpar{\reach{A}\mpar{s} \wedge \bigwedge_{v_1 \in V_1} v_{1'} = v_1}\psubst{\psi \uplus \psi_1} \\
-		\iff & \sigma \uplus \nu \vdash \reach{A}\mpar{s}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1} \psi_{1'}\mpar{v_{1'}} = \psi_1\mpar{v_1} \\
-		\impliedby & \sigma \uplus \nu \vdash \reach{A}\mpar{s}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1 \uplus \fvars{t_1}} v_{1'} = v_1 \\
-		\iff & \mpar{\sigma \vdash \reach{A}\mpar{s}\psubst{\psi}} \wedge \mpar{\sigma \uplus \nu \vdash \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1}
-	\end{align*}
+		\iff & \sigma \uplus \nu \vdash \mpar{\reach{A}\mpar{s'} \wedge \bigwedge_{v_1 \in V_1} v_{1'} = v_1}\psubst{\psi_{1'} \uplus \psi_2 \uplus \psi_1} \\
+		\iff & \sigma \uplus \nu \vdash \reach{A}\mpar{s'}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1} \psi_{1'}\mpar{v_{1'}} = \psi_1\mpar{v_1} \\
+		\iff & \mpar{\sigma \vdash \reach{A}\mpar{s'}\psubst{\psi}} \wedge \mpar{\sigma \uplus \nu \vdash \bigwedge_\subbox{v_1 \in V_1} \psi_{1'}\mpar{v_{1'}} = \psi_1\mpar{v_1}}
+	\end{align*}
+	For the left side we use the preservation of reachability across transitions:
+	\[ \forall t \defobject \OTg \in T, \fvars{t} \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi} \hyp{2} \]
+	\hyp{2} is used for transition \(t\) with valuation \(\sigma\), the left side of the implication is \hyp{1a} and \hyp{1c}.
+	For the right side, the variables of \(\psi\) are in \(V_1 \uplus \fvars{t_1}\) so proving the following is sufficient:
+	\[ \sigma \uplus \nu \vdash \bigwedge_\subbox{v_1 \in V_1 \uplus \fvars{t_1}} v_{1'} = v_1 \goal{2d'} \]
+	By renaming of the definition domain, \(\nu\) coincides with \(\sigma\) on \(\fvars{t_1}\).
+	For the other variables we use \hyp{1b}.
 \item[\goal{1}:] Let \nmm{\sigma: V \uplus V_1 \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
@@
 	\begin{gather}
-		\sigma \vdash \reach{A}\mpar{s} \hyp{2a} \\
-		\sigma \vdash \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1 \hyp{2b} \\
-		\sigma \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{2c}
+		\sigma \vdash \reach{A}\mpar{s} \hyp{3a} \\
+		\sigma \vdash \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1 \hyp{3b} \\
+		\sigma \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{3c}
 	\end{gather}
 	\(\reach{A}\) is a witness of the non-locking composition so we have the hypothesis:
-	\[ V \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{3} \]
-	We use \hyp{3} with valuation \(\sigma\) to get \nmm{\nu: \biguplus_\subbox{t \in \fOT{s}} \fvars{t} \to \values}.
-	The left side of the implication is proved with \hyp{2a} and \hyp{2c}, the right side gives the hypothesis:
-	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{3'} \]
-	We prove \goal{1} with valuation \(\nu\) by admitting the left side of the implication and using \hyp{3'}.
+	\[ V \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{4} \]
+	We use \hyp{4} with valuation \(\sigma\) to get \nmm{\nu: \biguplus_\subbox{t \in \fOT{s}} \fvars{t} \to \values}.
+	The left side of the implication is proved with \hyp{3a} and \hyp{3c}, the right side gives the hypothesis:
+	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{4'} \]
+	We prove \goal{1} with valuation \(\nu\) by admitting the left side of the implication and using \hyp{4'}.
 \end{proof}
@@
 \end{prop}
-% TODO: Renaming
 Let \(\OAg[3] \defobject A_3\) and \(A \defobject A_1\subst{A_3}{k}\), with \(\OAg \defobject A\).
@@
 \[ R \defobject \mpar{\mpar{s_1, s_3}, s_2} \mapsto R_{12}\mpar{s_1, s_2} \wedge \reach{A}\mpar{s_1, s_3} \]
-% END TODO
 We want to prove that \(R\) is a hole-superset simulation of \(A\) by \(A_2\).
@@
 	\goal{2c} is proved by \hyp{4c}.
-	For \goal{2d} we use \hyp{4d} and \hyp{3b} with the preservation of reachability across transitions:
+	For \goal{2d} we first perform a transformation.
 	\begin{align*}
 		& \sigma \uplus \nu \vdash R\mpar{s', s'_{2x}}\psubst{\psi \uplus \psi_{2x}} \\
-		\iff & \sigma \uplus \nu \vdash \mpar{R_{12}\mpar{s'_1, s'_{2x}} \wedge \reach{A}\mpar{s}}\psubst{\psi_1 \uplus \psi_{2x} \uplus \psi_3} \\
-		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \reach{A}\mpar{s}\psubst{\psi}}
-	\end{align*}
+		\iff & \sigma \uplus \nu \vdash \mpar{R_{12}\mpar{s'_1, s'_{2x}} \wedge \reach{A}\mpar{s'}}\psubst{\psi_1 \uplus \psi_{2x} \uplus \psi_3} \\
+		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \reach{A}\mpar{s'}\psubst{\psi}}
+	\end{align*}
+	The left side is \hyp{4d}.
+	For the right side we use the preservation of reachability across transitions:
+	\[ \forall t \defobject \OTg \in T, \fvars{t} \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi} \hyp{5} \]
+	\hyp{5} is used for transition \(t\) with valuation \(\sigma\), the left side of the implication is \hyp{3b} and \hyp{3c}.
 \item[\goal{1}:]
@@
 	\begin{gather}
-		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{5a} \\
-		\sigma \vdash \reach{A}\mpar{s} \hyp{5b} \\
-		\sigma \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{5c}
+		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{6a} \\
+		\sigma \vdash \reach{A}\mpar{s} \hyp{6b} \\
+		\sigma \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{6c}
 	\end{gather}
@@
 	\begin{gather}
-		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6} \\
-		V \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{7}
-	\end{gather}
-	We use \hyp{6} with valuation \(\sigma\) to get \nmm{\nu: \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
-	The left side of the implication is proved with \hyp{5a} and \hyp{5c}, the right side gives the hypothesis:
-	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{6'} \]
-	We then use \hyp{7} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t \in \fOT{s}} \fvars{t}}.
-	The left side of the implication is proved using \hyp{5b} and \hyp{6'}, the right side gives:
-	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{7'} \]
-	We prove \goal{1} with valuation \(\nu'\) by admitting the left side of the implication and using \hyp{7'}.
+		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{7} \\
+		V \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{8}
+	\end{gather}
+	We use \hyp{7} with valuation \(\sigma\) to get \nmm{\nu: \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
+	The left side of the implication is proved with \hyp{6a} and \hyp{6c}, the right side gives the hypothesis:
+	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{7'} \]
+	We then use \hyp{8} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t \in \fOT{s}} \fvars{t}}.
+	The left side of the implication is proved using \hyp{6b} and \hyp{7'}, the right side gives:
+	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{8'} \]
+	We prove \goal{1} with valuation \(\nu'\) by admitting the left side of the implication and using \hyp{8'}.
 \end{proof}
@@
 \end{thm}
-% TODO: Renaming
 Let \(A_{13} \defobject A_1\subst{A_3}{k}\) and \(A_{23} \defobject A_2\subst{A_3}{k}\).
+Let \(v_3 \mapsto v_{3x}\) is the renaming for \(v_3 \in V_3\) in \(A_{x3}\).
 We pose \(\OAg[13] \defobject A_{13}\) and \(\OAg[23] \defobject A_{23}\).
@@
 \[ R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \]
-Where \(y_3 \mapsto y_{3x}\) is the renaming for \(y\) a variable or a valuation of \(A_3\) in \(A_{x3}\).
-% END TODO
 We want to prove that \(\mpar{R, H}\) is a witness of \(\wrel{A_{13}}{A_{23}}{H}\).
@@
 	For \goal{3c} we have two cases, if \(k \notin J'_1\) then \(g_{23x} \iff g_{2x}\) and \hyp{3c} is sufficient, if \(k \in J'_1\) then \(g_{23x} \iff g_{2x} \wedge g_3 \wedge \alpha_3 = \beta_{2xk}\) so we also need \hyp{2d} (\(g_{13} \iff g_1 \wedge g_3 \wedge \alpha_3 = \beta_{1k}\)) and \hyp{3b} for the value \(k\) (\(\beta_{1k} = \beta_{2xk}\)).
-	\goal{3d} is proved using \hyp{3d}, \hyp{2b} with the preservation of reachability across transitions (+ \hyp{2d}), \hyp{2c} and the fact that \(A_3\) performs the same transition with same values in both composed automata:
+	For \goal{3d} we first perform a transformation.
 	\begin{align*}
@@
 		\iff & \sigma \uplus \nu' \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}} \wedge \bigwedge_\subbox{v_3 \in V_3} \psi_{31}\mpar{v_{31}} = \psi_{32}\mpar{v_{32}} \\
-		\impliedby & \sigma \uplus \nu' \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}} \wedge \bigwedge_\subbox{v_3 \in V_3 \uplus \fvars{t_3}} v_{31} = v_{32} \\
-		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}}} \wedge \mpar{\sigma \vdash \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32}}
-	\end{align*}
+		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}}} \wedge \mpar{\sigma \uplus \nu' \vdash \bigwedge_\subbox{v_3 \in V_3} \psi_{31}\mpar{v_{31}} = \psi_{32}\mpar{v_{32}}}
+	\end{align*}
+	The left side is \hyp{3d}.
+	For the middle part we use the preservation of reachability across transitions:
+	\[ \forall t_{13} \defobject \OTx{13}{}{13}{13} \in T_{13}, \fvars{t_{13}} \vdash \reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}} \hyp{4} \]
+	\hyp{4} is used for transition \(t_{13}\) with valuation \(\sigma\), the left side of the implication is \hyp{2b} and \hyp{2d}.
+
+	For the right side, the variables of \(\psi_{13}\) and \(\psi_{23}\) are renaming of \(\psi_3\) on variables in \(\fvars{t_3}\) or do not involve these variables at all, so either \hyp{2c} is sufficient, or additionnaly proving the following is sufficient:
+	\[ \nu' \vdash \bigwedge_\subbox{v_3 \in \fvars{t_3}} v_{31} = v_{32} \]
+	Which holds by definition of \(\nu'\).
 \item[\goal{1}:] Let \nmm{\sigma: V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \to \values}.
@@
 	\begin{gather}
-		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{4a} \\
-		\sigma \vdash \reach{A_{13}}\mpar{s_{13}} \hyp{4b} \\
-		\sigma \vdash \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \hyp{4c}
+		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{5a} \\
+		\sigma \vdash \reach{A_{13}}\mpar{s_{13}} \hyp{5b} \\
+		\sigma \vdash \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \hyp{5c}
 	\end{gather}
@@
 	\begin{gather}
-		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{5} \\
-		V_{13} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{6}
-	\end{gather}
-	We use \hyp{5} with valuation \(\sigma\) projected on the variables from generating transitions in \(A_2\) to get \nmm{\nu: \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
-	The left side of the implication is proved using \hyp{4a} and \hyp{4c} because the guards from transitions of \(A_2\) are still in transitions of \(A_{23}\), the right side gives:
-	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{5'} \]
-	We then use \hyp{6} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}}}.
-	The left side of the implication is proved using \hyp{4b} and \hyp{5'}, the right side gives:
-	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{6'} \]
-	\goal{1} is proved for valuation \(\nu'\) by admitting the left side and using \hyp{6'}.
+		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6} \\
+		V_{13} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{7}
+	\end{gather}
+	We use \hyp{6} with valuation \(\sigma\) projected on the variables from generating transitions in \(A_2\) to get \nmm{\nu: \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
+	The left side of the implication is proved using \hyp{5a} and \hyp{5c} because the guards from transitions of \(A_2\) are still in transitions of \(A_{23}\), the right side gives:
+	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6'} \]
+	We then use \hyp{7} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}}}.
+	The left side of the implication is proved using \hyp{5b} and \hyp{6'}, the right side gives:
+	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{7'} \]
+	\goal{1} is proved for valuation \(\nu'\) by admitting the left side and using \hyp{7'}.
 \end{proof}
@@
 \end{thm}
-% TODO: Renaming
 We pose \(\OAg[21] \defobject A_{21}\) and \(\OAg[31] \defobject A_{31}\).
+Let \(v_1 \mapsto v_{1x}\) is the renaming for \(v_1 \in V_1\) in \(A_{x1}\).
 The idea for the relation on configurations is that \(A_3\) simulates \(A_2\) while \(A_1\) does the same things in both compositions.
 \[ R \defobject \mpar{\mpar{s_{12}, s_2}, \mpar{s_{13}, s_3}} \mapsto \choice{R_{23}\mpar{s_2, s_3} \wedge \reach{A_{21}}\mpar{s_{12}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{12} = v_{13} & \text{if } s_{12} = s_{13} \\ \bot & \text{otherwise}} \]
-Where \(y_1 \mapsto y_{1x}\) is the renaming for \(y\) a variable or a valuation of \(A_1\) in \(A_{x1}\).
-% END TODO
 We want to prove that \(\mpar{R, H}\) is a witness of \(\wrel{A_{21}}{A_{31}}{H}\).
@@
 	For \goal{3c} we have two cases, if \(k \notin J'_{12}\) then \(g_{31x} \iff g_{13}\) and \hyp{2d} is sufficient (\(g_{21} \iff g_{13}\)), if \(k \in J'_{13}\) then \(g_{31x} \iff g_{13} \wedge g_{3x} \wedge \alpha_{3x} = \beta_{13k}\) so we also need \hyp{3c} and \hyp{3a} in addition to \hyp{2d} (\(g_{21} \iff g_{13} \wedge \alpha_2 = \beta_{12k}\)).
-	\goal{3d} is proved using \hyp{3d}, \hyp{2b} with the preservation of reachability across transitions (+ \hyp{2d}), \hyp{2c} and the fact that \(A_1\) performs the same transition with same values in both composed automata:
+	For \goal{3d} we first perform a tranfsformation.
 	\begin{align*}
@@
 		\iff & \sigma \uplus \nu' \vdash R_{23}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}} \wedge \reach{A_{21}}\mpar{s'_{21}}\psubst{\psi_{21}} \wedge \bigwedge_\subbox{v_1 \in V_1} \psi_{12}\mpar{v_{12}} = \psi_{13}\mpar{v_{13}} \\
-		\impliedby & \sigma \uplus \nu' \vdash R_{23}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}} \wedge \reach{A_{21}}\mpar{s'_{21}}\psubst{\psi_{21}} \wedge \bigwedge_\subbox{v_1 \in V_1 \uplus \fvars{t_1}} v_{12} = v_{13} \\
-		\iff & \mpar{\sigma \uplus \nu \vdash R_{23}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}} \wedge \mpar{\sigma \vdash \reach{A_{21}}\mpar{s'_{21}}\psubst{\psi_{21}}} \wedge \mpar{\sigma \vdash \bigwedge_\subbox{v_1 \in V_1} v_{12} = v_{13}}
-	\end{align*}
+		\iff & \mpar{\sigma \uplus \nu \vdash R_{23}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}} \wedge \mpar{\sigma \vdash \reach{A_{21}}\mpar{s'_{21}}\psubst{\psi_{21}}} \wedge \mpar{\sigma \uplus \nu' \vdash \bigwedge_\subbox{v_1 \in V_1} \psi_{12}\mpar{v_{12}} = \psi_{13}\mpar{v_{13}}}
+	\end{align*}
+	The left side is \hyp{3d}.
+	For the middle part we use the preservation of reachability across transitions:
+	\[ \forall t_{21} \defobject \OTx{21}{}{21}{21} \in T_{21}, \fvars{t_{21}} \vdash \reach{A_{21}}\mpar{s_{21}} \wedge g_{21} \implies \reach{A_{21}}\mpar{s'_{21}}\psubst{\psi_{21}} \hyp{4} \]
+	\hyp{4} is used for transition \(t_{21}\) with valuation \(\sigma\), the left side of the implication is \hyp{2b} and \hyp{2d}.
+
+	For the right side, the variables of \(\psi_{12}\) and \(\psi_{13}\) are renaming of \(\psi_1\) on variables in \(\fvars{t_1}\) so proving the following is sufficient:
+	\[ \sigma \vdash \bigwedge_\subbox{v_1 \in V_1 \uplus \fvars{t_1}} v_{12} = v_{13} \goal{2d'} \]
+	Which holds by \hyp{2c} and by definition of \(\nu'\) for variables of the transition.
 \item[\goal{1}:] Let \nmm{\sigma: V_{21} \uplus V_{31} \uplus \biguplus_\subbox{t_{31} \in \fOT{s_{31}}} \fvars{t_{31}} \to \values}.
@@
 	\begin{gather}
-		\sigma \vdash R_{23}\mpar{s_2, s_3} \hyp{4a} \\
-		\sigma \vdash \reach{A_{21}}\mpar{s_{21}} \hyp{4b} \\
-		\sigma \vdash \bigvee_\subbox{t_{31} \in \fOT{s_{31}}} \fguard{t_{31}} \hyp{4c}
+		\sigma \vdash R_{23}\mpar{s_2, s_3} \hyp{5a} \\
+		\sigma \vdash \reach{A_{21}}\mpar{s_{21}} \hyp{5b} \\
+		\sigma \vdash \bigvee_\subbox{t_{31} \in \fOT{s_{31}}} \fguard{t_{31}} \hyp{5c}
 	\end{gather}
@@
 	\begin{gather}
-		V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash R_{23}\mpar{s_2, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{5} \\
-		V_{21} \uplus \biguplus_\subbox{t_{12} \in \fOT{s_{12}}} \fvars{t_{12}} \vdash \reach{A_{21}}\mpar{s_{21}} \wedge \bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}} \implies \bigvee_\subbox{t_{21} \in \fOT{s_{21}}} \fguard{t_{21}} \hyp{6}
-	\end{gather}
-	We use \hyp{5} with valuation \(\sigma\) to get \nmm{\nu: \biguplus_\subbox{t_{12} \in \fOT{s_{12}}} \fvars{t_{12}} \to \values}.
-	The left side of the implication is proved using \hyp{4a} and \hyp{4c} because the guards from transitions of \(A_3\) are still in transitions of \(A_{31}\), the right side gives:
-	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{5'} \]
-	We then use \hyp{6} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t_{21} \in \fOT{s_{21}}} \fvars{t_{21}}}.
-	The left side of the implication is proved using \hyp{4b} and \hyp{5'}, the right side gives:
-	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t_{21} \in \fOT{s_{21}}} \fguard{t_{21}} \hyp{6'} \]
-	\goal{1} is proved for valuation \(\nu'\) by admitting the left side and using \hyp{6'}.
+		V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash R_{23}\mpar{s_2, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{6} \\
+		V_{21} \uplus \biguplus_\subbox{t_{12} \in \fOT{s_{12}}} \fvars{t_{12}} \vdash \reach{A_{21}}\mpar{s_{21}} \wedge \bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}} \implies \bigvee_\subbox{t_{21} \in \fOT{s_{21}}} \fguard{t_{21}} \hyp{7}
+	\end{gather}
+	We use \hyp{6} with valuation \(\sigma\) to get \nmm{\nu: \biguplus_\subbox{t_{12} \in \fOT{s_{12}}} \fvars{t_{12}} \to \values}.
+	The left side of the implication is proved using \hyp{5a} and \hyp{5c} because the guards from transitions of \(A_3\) are still in transitions of \(A_{31}\), the right side gives:
+	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{6'} \]
+	We then use \hyp{7} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t_{21} \in \fOT{s_{21}}} \fvars{t_{21}}}.
+	The left side of the implication is proved using \hyp{5b} and \hyp{6'}, the right side gives:
+	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t_{21} \in \fOT{s_{21}}} \fguard{t_{21}} \hyp{7'} \]
+	\goal{1} is proved for valuation \(\nu'\) by admitting the left side and using \hyp{7'}.
 \end{proof}

### 2021-06-23 2021-Refinement/report.tex
Minor corrections

@@
 	\end{align*}
-	For the left side we use the preservation of reachability across transitions:
+	For the left side we use the definition of reachability (reachability is preserved across transitions):
 	\[ \forall t \defobject \OTg \in T, \fvars{t} \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi} \hyp{2} \]
@@
 	The left side is \hyp{4d}.
-	For the right side we use the preservation of reachability across transitions:
+	For the right side we use the definition of reachability (reachability is preserved across transitions):
 	\[ \forall t \defobject \OTg \in T, \fvars{t} \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi} \hyp{5} \]
@@
 Let \(A_{13} \defobject A_1\subst{A_3}{k}\) and \(A_{23} \defobject A_2\subst{A_3}{k}\).
-Let \(v_3 \mapsto v_{3x}\) is the renaming for \(v_3 \in V_3\) in \(A_{x3}\).
+Let \(v_3 \mapsto v_{3x}\) be the renaming for \(v_3 \in V_3\) in \(A_{x3}\).
 We pose \(\OAg[13] \defobject A_{13}\) and \(\OAg[23] \defobject A_{23}\).
@@
 	The left side is \hyp{3d}.
-	For the middle part we use the preservation of reachability across transitions:
+	For the middle part we use the definition of reachability (reachability is preserved across transitions):
 	\[ \forall t_{13} \defobject \OTx{13}{}{13}{13} \in T_{13}, \fvars{t_{13}} \vdash \reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}} \hyp{4} \]
@@
 We pose \(\OAg[21] \defobject A_{21}\) and \(\OAg[31] \defobject A_{31}\).
-Let \(v_1 \mapsto v_{1x}\) is the renaming for \(v_1 \in V_1\) in \(A_{x1}\).
+Let \(v_1 \mapsto v_{1x}\) be the renaming for \(v_1 \in V_1\) in \(A_{x1}\).
 The idea for the relation on configurations is that \(A_3\) simulates \(A_2\) while \(A_1\) does the same things in both compositions.
@@
 	The left side is \hyp{3d}.
-	For the middle part we use the preservation of reachability across transitions:
+	For the middle part we use the definition of reachability (reachability is preserved across transitions):
 	\[ \forall t_{21} \defobject \OTx{21}{}{21}{21} \in T_{21}, \fvars{t_{21}} \vdash \reach{A_{21}}\mpar{s_{21}} \wedge g_{21} \implies \reach{A_{21}}\mpar{s'_{21}}\psubst{\psi_{21}} \hyp{4} \]

### 2021-06-25 2021-Refinement/report.tex
Small fixes suggested by Rabea's collegue Sophie

@@
 Families of values, or equivalently maps will be noted \(\mset{i \mapsto x_i}{i \in I}\), \(\mset{i \gets x_i}{i \in I}\) or \(x_i^{i \in I}\).
+% TODO: introduire le fait que \exists c_j^{j \in J} défini J et {j \mapsto c_j}
 For instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\).
@@
 This allows the synchronisation of the two holes to be hidden to the exterior by sending a \(\tau\).
-However here \(\tau\) is not always allowed from the holes, for instance in the state \(L\) the hole \(r\) cannot emit it.
+However here \(\tau\) is not always allowed from the holes, for instance in the state \(L\) the hole \(r\) cannot emit it because there is no transition allowing this action from this hole.
 These transitions have been omitted for the sake of simplifying the first example of open automata.
@@
 The action emitted when \(A_c\) makes a transition is synchronised with the action of the hole \(k\) in transitions of \(A_p\) which have it as a hole action (first transition set, \(\alpha_c = \beta_k\)).
-The composition may look like a handshake, with both automata running in parallel (product of states and joint variables) however it is asymmetric because it is the first automaton that decides when the second can evolve, while the first automaton can evolve independently as soon as the hole is not involved in the open transition considered.
+The composition may look like a handshake, with both automata running in parallel (product of states and joint variables) however it is asymmetric:
+The first automaton decides when the second can evolve by involving it in a transition, while the first automaton can evolve independently as soon as the hole is not involved in an open transition.
 \begin{exi}\label{exi:full_comp}
@@
 
-Two states \(s_1 \in S_1, s_2 \in S_2\) with their respective valuations \(\sigma_1: V_1 \to \values, \sigma_2: V_2 \to \values\) are related iff \(\sigma_1 \uplus \sigma_2 \vdash R\mpar{s_1, s_2}\).
+Two configurations \(\mpar{s_1, \sigma_1} \in S_1 \mpar{V_1 \to \values}, \mpar{s_2, \sigma_2} \in S_2 \times \mpar{V_2 \to \values}\) are related iff \(\sigma_1 \uplus \sigma_2 \vdash R\mpar{s_1, s_2}\).
 \end{defi}
@@
 \defitem \textbf{correct w.r.t.\@ composition} iff \(\forall a\, b, a\subst{b}{j} \leq a\);
-\defitem \textbf{complete w.r.t.\@ composition} iff \(\forall a\, b, a \leq b \implies \exists c, a \cong b\subst{c}{j}\);
+\defitem \textbf{complete w.r.t.\@ composition} iff \(\forall a\, b, a \leq b \implies \exists c_j^{j \in J}, a \cong b\mdbrk{c_j^{j \in J}}\);
 \defitem \textbf{context refining for composition} iff \(\forall a\, b\, c, a \leq b \implies a\subst{c}{j} \leq b\subst{c}{j}\);
@@
 The first part is the main requirement, a stronger version of the pre-simulation requirement so that it better fits SMT.
-Instead of matching an instanciated transition to another instanciated transition as in the pre-simulation definition, we match an open transition to a family of covering open-transitions.
+Instead of matching an instanciated transition to another instanciated transition as in the pre-simulation definition, we match the open transition \(t_1\) to the family of covering open transitions \(t_{2x}^{x \in X}\) to account for all instanciations of \(t_1\).
 The second part is directly the deadlock reduction requirement.

### 2021-07-05 2021-Refinement/paper/refinementarticle.tex
init paper refinement

--- 2021-06-23 2021-Refinement/report.tex
@@
-\documentclass{article}
+\documentclass[runningheads]{llncs}
 
-\usepackage{xunicode}
-\usepackage{fontspec}
-\usepackage[hmargin=3cm]{geometry}
+\usepackage{tikz}
+
 \usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{unicode-math}
+%\usepackage{amsthm}
+%\usepackage{unicode-math}
 \usepackage{tikz}
 \usetikzlibrary{external}
-\usepackage[final,hidelinks]{hyperref}
+\usepackage{hyperref}
 \AtBeginDocument{\renewcommand\setminus{\smallsetminus}}
-\usepackage{polyglossia}
-\setmainlanguage{english}
 
@@
 
-\title{Refinement for open automata}
-\author{Quentin \textsc{Corradi}}
+\begin{document}
+%
+\title{Refinements for open pNets}
+%
+%\titlerunning{Abbreviated paper title}
+% If the paper title is too long for the running head, you can set
+% an abbreviated paper title here
+%
+\author{
+Rabéa\inst{1}\orcidID{1111-2222-3333-4444} \and
+Quentin\inst{1,2}\orcidID{1111-2222-3333-4444} \and
+Ludo\inst{2}\orcidID{0000-1111-2222-3333} \and
+Eric\inst{3}\orcidID{2222--3333-4444-5555}}
+%
+\authorrunning{Rabéa Ameur-Boulifa et al.}
+% First names are abbreviated in the running head.
+% If there are more than two authors, 'et al.' is used.
+%
+\institute{blabla
+\email{lncs@fff}\\
+\url{http://www.springer.com/gp/computer-science/lncs} \and
+blibli\\
+\email{\{abc,def\}@fff}}
+%
+\maketitle              % typeset the header of the contribution
+%
+\begin{abstract}
+The abstract should briefly summarize the contents of the paper in
+150--250 words.
 
-\begin{document}
-\maketitle
+\keywords{Labelled transition systems  \and Refinement \and Composition.}
+\end{abstract}
+%
+%
+%
+\section{Introduction}
+\TODO{1.5 pages}
 
-\section{Introduction}
-The open automata model was originally designed to give the semantic of open pNets \cite{2007.10770}.
-Open pNets are not petri nets but an intermediate representation used in the VerCors project to perform verification of concurrent systems \cite{henrio:01252323}.
-Verification is the process of checking properties on a description in a specific model (for instance classical automata).
-A particular kind of verification are refinement relations.
+\section{Related Work}
+\label{sec:sota}
 
-Refinement relations verify that and implementation satisfies some properties with respect to a specification.
-The open pNets model is based around a hierarchical composition of generalised automata.
-A property a refinement can check on them is the non introduction of deadlocks.
-A deadlock being an unintended state where no further action is possible.
+\TODO{1 page}
 
-The composition of open automata is inherited from open pNets as the open automaton generated from the composition on open pNets.
-This means that composition is only defined on open pNets and not directly on open automata.
-Open pNets with the open automaton semantics and equivalence relation introduced in previous work \cite{henrio:01299562} were sucessfully used to model and verify some properties of applications \cite{qin:01823507, ameurboulifa:01526055} based on BIP (Behaviour-Interaction-Priority) \cite{basu:hal-00722395} and GCM (Grid Component Model) \cite{baude:inria-00323919}.
-However only an equivalence relation was used.
-For instance a usecase on open pNet where equivalence is not sufficient can be found in an article about algorithms fo weak bisimulation on open automata \cite{wang:03126313}.
-
-The contributions of this report are:
-\begin{enumerate}
-\item The formalisation of composition for open automata without requiring open pNets.
-\item The translation of some properties of refinement relations from LTS to open automata.
-\item The characterisation of a composition that doesn't introduce deadlocks.
-\item The introduction of several refinement relations for open automata that behave nicely with composition.
-\end{enumerate}
-This report is organised as follows:
-We begin with Section \ref{sec:sota} by describing the state-of-the-art.
-Then there are several sections dedicated to define all the interesting objects and properties:
-In section \ref{sec:notations} we give some notations used throughout this paper.
-In Section \ref{sec:def} we give a clean and up to date definition of open automata.
-In Section \ref{sec:comp} we define their composition without requiring the use of open pNets.
-In Section \ref{sec:proofelts} we adapt to open automata several standard properties from refinement relations on LTS.
-After that Section \ref{sec:prelref} is dedicated to building refinement relations in the easy cases.
-Section \ref{sec:refinement} introduces and analyses the refinement relation on open automata.
-Finally Section \ref{sec:ccl} recapitulates the contribution and presents the work left.
-
-\section{Related work}\label{sec:sota}
 Previous work on open automata focused on equivalence relations compatible with composition.
@@
 
-\section{Notations}\label{sec:notations}
-Notations will be defined with the operator \(\defnotation\) and names are given with the operator \(\defobject\) as follows:
-\begin{align*}
-	\mathit{notation\_with\_variables} & \defnotation \mathit{notated\_object\_using\_the\_variables} \\
-	\mathit{name} & \defobject \mathit{fully\_defined\_mathematical\_object}
-\end{align*}
+\section{Background: Open Automata and their Composition}\label{sec:background}
+\TODO{3.5 pages}
 
-Throughout this paper, tuples will be noted differently depending on what they represent.
-This helps distinguishing the manipulated objects.
-Every such notation will be introduced in the definition of the object.
+\section{A First Refinement Relation}\label{sec:refinement}
+\TODO{4 pages}
 
-Families of values, or equivalently maps will be noted \(\mset{i \mapsto x_i}{i \in I}\), \(\mset{i \gets x_i}{i \in I}\) or \(x_i^{i \in I}\).
-For instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\).
-They will be used depending on what is more convenient.
-For instance \(\mbrc{\alpha \mapsto 1, \beta \mapsto 2, \gamma \mapsto 3}\) has no simple generating expression and is better represented with the finite version of first notation.
+\section{A Refinement Relation that Takes Holes into Account}\label{sec:holes}
+\TODO{3.5 pages}
 
-The disjoint union on set is noted \(\uplus\).
-There are several ways of ensuring a union is disjoint, we will indifferently either suppose sets are disjoint or rename conflicting object (useful for variables).
-The disjoint union of two maps \(\varphi: I \to X\) and \(\psi: J \to Y\) with \(I \cap J = \emptyset\) is noted \(\varphi \uplus \psi\) and has the following signature \(I \uplus J \to X \cup Y\).
-
-In a formula, a quantifier followed by a finite set will be used as a shorthand for the quantification on every variable in the set:
-\(\forall \mbrc{a_1, \dots, a_n}, \exists \mbrc{b_1, \dots, b_m}, P\) means \(\forall a_1, \dots, \forall a_n, \exists b_1, \dots, \exists b_m, P\).
-
-\section{Open Automata}\label{sec:def}
-To define the open automata we need some preliminary definitions.
-\begin{defi}[Expression algebra, Action algebra, Formulas, Terms]
-An expression algebra \(E\) is a disjoint union \(E \defobject \terms \uplus \actions \uplus \formulas\) of the terms, the actions and the formulas.
-
-Notations are parametrized by a term algebra \(\terms\).
-As any term algebra it has constant symbols with arity, variables, and a typing mechanism to distinguish well-formed and ill-formed terms.
-The action algebra \(\actions\) is another term algebra.
-The formulas \(\formulas\) are at least the first order formulas over \(\terms\) and \(\actions\).
-\end{defi}
-The term algebras are arbitrary.
-The formulas contain at least first order logic terms with an equality relation.
-This equality relation is not necessarily a syntactic equality (\(2 + 2 \neq 4\) with a syntactic equality but it is more expressive to consider that the two terms are equal).
-
-An example of term algebra can be Peano integers (constant zero with arity 0, constant successor function with arity 1 and the variables), the formulas associated can use syntactic equality relation, the sum relation \(\mathit{sum}\mpar{a, b, c}: \text{``}a = b + c\text{"}\), and the product relation \(\mathit{prod}\mpar{a, b, c}: \text{``}a = b \times c\text{"}\).
-\begin{defi}[Unbound variables, Expressions restricted to variables, Closed expressions]
-\defitem \(\fvars{e}\) is the set of variables in \(e \in E\) that are not bound by any binder.
-	Binders can be for instance quantifiers in formulas, or let-binders in terms if they are part of the term algebra.
-\defitem The expressions restricted to variables in \(V\) are \(E_V \defnotation \mset{e \in E}{\fvars{e} \subseteq V}\); \(E_V \subset E\).
-\defitem The closed expressions are expressions restricted to variables in \(\emptyset\), \(E_\emptyset\).
-\end{defi}
-Terms, actions and formulas restricted to variables and their closed versions are also defined by restriction.
-A closed expression can contain variables under a binder, only unbound variable are forbidden.
-
-We can use the previous example of first order formula on Peano integers to illustrate these definitions.
-\(x\), \(S\mpar{y}\) are well-formed terms, \(0\) is a closed term, \(\fvars{x} = \mbrc{x}\), \(\fvars{S\mpar{y}} = \mbrc{y}\), \(\fvars{0} = \emptyset\).
-\(x = 0\), \(\forall y, \exists x, \mathit{sum}\mpar{y, z, x}\) are valid formulas, \(\forall x, \neg S\mpar{x} = 0\) is a valid closed formula, \(\fvars{x = 0} = \mbrc{x}\), \(\fvars{\forall y, \exists x, \mathit{sum}\mpar{y, z, x}} = \mbrc{z}\), \(\fvars{\forall x, \neg S\mpar{x} = 0} = \emptyset\).
-\begin{defi}[Values, Satisfiability, (Parallel) substitution]
-We assume that the following are given:
-\defitem The values \(\values\), which are interpretations of closed terms.
-\defitem The satisfiability relation on closed formulas, \({\vdash} f\) where \(f \in \rformulas\).
-\defitem The substitution in \(e \in E\) of \(x \in \fvars{e}\) by \(t \in \terms\), \(e\subst{t}{x}\).
-\defitem The parallel substitution in \(e \in E\) of variables in \(V\) by \(\psi: V \to \terms\), \(e\psubst{\psi}\).
-\end{defi}
-For the parallel substitution, the set \(V\) is not required to be a subset of \(\fvars{e}\).
-In the case it isn't, the variables in \(V \setminus \fvars{e}\) are not substituted.
-The substitutions might give a ill-formed expression; for instance let the terms be integers and pairs with (pointwise) addition, \(\mpar{a + b}\psubst{a \mapsto 7, b \mapsto \mpar{4, 5}}\) is a ill-formed term.
-This can be guarded with the check \(e\subst{t}{x} \in E\) and \(e\psubst{\psi} \in E\) and it will implicitly be the case, for instance when there is quantification on \(t\) and \(\psi\), to simplify notations.
-
-The interpretation of terms is supposed to be decidable.
-The satisfiability of formulas might not be decidable nor complete nor consistent,
-but we will consider in the following that they are; this can be achieved by restricting the term algebra to a decidable subset.
-For instance a formula with quantifiers on variables might not be provable even if it is true for all values of these variables.
-In practice the formulas will be given to a SMT solver and we cannot always make sure they have all the previous properties but, at least any property found satisfiable by the SMT is ensured to be true.
-\(\vdash\) can hence be interpreted as an indicator of what is given to the SMT; it separates the external logic and the logic on \(\formulas\).
-
-Values will be used for keeping a variable state, and then injected in terms for substitution.
-This is correct when \(\values \subseteq \rterms\) and we suppose it is the case.
-Otherwise this doesn't invalidates theorems because substitution by a value can stand as a shorthand for substitution with any term which has the value as an interpretation.
-We suppose that the interpretation of terms is compatible w.r.t.\@ substitution, that is if two terms \(t\), \(t'\) are interpreted with the same value, then replacing \(t\) by \(t'\) in a well-formed expression makes an equivalent well-formed expression.
-\begin{noti}[Notations for separating external logic and logic on \(\formulas\)]
-\defitem The satisfiability of a formula \(f \in \formulas\) under some valuation \(\sigma: V \to \values\) is noted:
-\[ \sigma \vdash f \defnotation \vdash \exists \fvars{f\psubst{\sigma}}, f\psubst{\sigma} \]
-\defitem The satisfiability of a formula \(f \in \formulas\) with some variable set \(V\) as context is noted:
-\[ V \vdash f \defnotation \vdash \forall V, \exists\mpar{\fvars{f} \setminus V}, f \]
-\defitem The precedence of \(\vdash\) is the lowest on the right side and higher than \(\uplus\) on the left side:
-\[ \forall a \, b, a \uplus b \vdash x \wedge y \implies \exists z, P\mpar{x,z} \text{ is the same as } \forall a \, b, \bigg((a \uplus b) \vdash \Big((x \wedge y) \implies \exists z, P\mpar{x,z}\Big)\bigg) \]
-\end{noti}
-With these common definitions and notations settled, the objects of interest can now be defined.
-\begin{defi}[Open automaton]
-An open automaton is a tuple \(\OAg\) with \(S\) the set of states, \(s_0 \in S\) the initial state, \(V\) the set of variable names unique to this automaton, \(\sigma_0: V' \to \values\) the initial valuation of variables where \(V' \subseteq V\), \(J\) the set of hole names and \(T\) the set of open transitions.
-A pair of a state and a valuation is called a configuration.
-
-\(S, V, J\) are arbitrary finite sets. % OR finite arbitrary sets?
-\end{defi}
-The variable names may clash when considering two automata, in this case we suppose that we can still distinguish the variables in the formulas.
-In practice the open automata are used in a toolchain that guarantees there are no name clash.
-
-The initial valuation is a partial valuation of the variables.
-If an undefined variable is set before being read, it behaves like an initially set variable.
-If an undefined variable is not set before being read then its value may be any fixed value.
-When we will introduce refinements in Section \ref{sec:prelref}, setting an undefined variable will be considered a valid refinement, for instance a \(5\) bits register is a particular \(n\) bits register.
-\begin{defi}[Open transition, Instanciated transition]
-An open transition is a tuple \nmm{\OTg} with \(s, s' \in S\) the source and target states, \(\alpha \in \actions\) the produced action, \(J' \subseteq J\) the holes involved in the transition, \(\beta_j \in \actions\) the actions of the holes, \(g \in \formulas\) the guard and \(\psi: V \to \terms\) the variable assignments.
-An open transition can have many unbound variables.
-
-An instanciated transition of the automaton is transition produced by any well-formed substitution of the unbound variables of the transition minus the automaton variables.
-\end{defi}
-The intuition of an open automaton is a partially defined LTS with variables, guards on transitions, and parametrised actions.
-The LTS is partial in the sense that one can plug an LTS in the hole and the surrounding LTS will react to the actions emitted by the sub-LTS put in the hole.
-Initially the automaton is in the initial state with an extension on all the variables of the initial valuation.
-In any configuration, it can perform instanciated transitions which source state is the current state and which guard is satisfiable in the current valuation if the holes emit the indicated actions.
-An instanciated transition is a transition where every variable that is not an automaton variable is instantiated with a value.
-By performing the instanciated transition, the automaton emits the indicated action and updates its configuration according to the target state and variable assignments.
-\begin{noti}[FH-bisimulation]
-The FH-bisimulation \cite{henrio:01055091} is noted \(\cong\).
-
-The FH-bisimulation is currently the only equivalence relation on open automata.
-The definition is not important, but the interested reader can check the article cited.
-\end{noti}
-To illustrate these definitions we consider two implementations (figure \ref{fig:enable}) of the LOTOS \cite{ISOLOTOS} operator enable in the open automata model.
-The enable operator runs the left hand side agent until it chooses to finish, at which point it produces an action \(\delta\mpar{t}\) (with \(t\) some data) that is synchronised with the first action of the right hand side agent which must be \(\act{accept}\mpar{t}\) (here \(t\) is an input), then only the latter agent runs.
-The \(\act{accept}\) action is shortened as \(\act{acc}\) in the examples.
-During the synchronised action, the value returned by the first agent is passed to the second agent.
-\begin{exi}[Enable, state-oriented]
-Graphical convention for drawing automata are as follows.
-As standard automata, circles represent states and simple arrows represent transitions.
-The initial state is indicated by a double circle.
-States names are indicated inside the circles and transitions labels are drawn near their corresponding arrow.
-The open transitions do not indicate the source and target states since that is the role of the transitions arrows; only the emitted action is on the bottom side of open transitions.
-Initial valuations are indicated near a double lined arrow pointing to the initial state.
-\begin{figure}
-\centering
-\input{enable_state.tex}
-\vrule
-\input{enable_var.tex}
-\caption{Enable operator implementation with open automata, on the left state oriented, on the right data oriented}
-\label{fig:enable}
-\end{figure}
-The automaton on the left side of the figure is \(\OA{\mbrc{L, R}}{L}{\emptyset}{\mbrc{}}{\mbrc{l, r}}{T}\) where transitions in \(T\) are:
-\begin{align*}
-	\OT{L}{L}{x}{\mbrc{l \mapsto x}}{\forall y, x \neq \delta\mpar{y}}{\mbrc{}} &&
-	\OT{L}{R}{\tau}{\mbrc{l \mapsto \delta\mpar{x}, r \mapsto \act{acc}\mpar{y}}}{x = y}{\mbrc{}} &&
-	\OT{R}{R}{x}{\mbrc{r \mapsto x}}{\top}{\mbrc{}}
-\end{align*}
-Note that the transition in the middle could have been expressed as \(\mbrc{l \mapsto \delta\mpar{x}, r \mapsto \act{acc}\mpar{x}}\).
-It would have avoided many instanciated transitions with trivially false guards like the one where \(x \mapsto 1, y \mapsto 2\), which has the guard \(1 = 2\).
-
-This automaton is an implementation of the enable operator because it begins in the state \(L\), where it allows any non \(\delta\) transition from its hole \(l\), then the automaton synchronises its holes on the same data, effectively allowing a data exchange when it goes into state \(R\), and finally allows any transition from its hole \(r\).
-The implementation of value passing in the open automata model doesn't distinguish input and output variables as in LOTOS.
-Both holes must emit their actions with valid data to perform the transition in the enable operator.
-If it is not possible the system is locked.
-
-We use the standard convention that uses \(\tau\) as a non-observable transition, never synchronised with other actions and passed unmodified.
-This allows the synchronisation of the two holes to be hidden to the exterior by sending a \(\tau\).
-However here \(\tau\) is not always allowed from the holes, for instance in the state \(L\) the hole \(r\) cannot emit it.
-These transitions have been omitted for the sake of simplifying the first example of open automata.
-\end{exi}
-Finally we can define some useful functions:
-\begin{defi}[Guard, Out-transition, Transition variables]
-Let \(V\) be the variable names of the considered automaton, \(T\) its transitions and \(r\) one of its states.
-\(\fOT[T]{r} \in T\) are called the out-transitions of the state \(r\).
-\(\fIT[T]{r} \in T\) are called the in-transitions of the state \(r\).
-When the transition set is clear from the context, it will be omitted.
-The local variables of a transition \(\fvars{t}\) are all variables appearing in transition \(t\) except the global variables of the automaton.
-\begin{align*}
-	\fOT[T]{r} & \defnotation \mset{\OTg \in T}{s = r} &
-	\fIT[T]{r} & \defnotation \mset{\OTg \in T}{s' = r} \\
-\end{align*}
-\vspace{-1cm}
-\begin{gather*}
-	\fguard{\OTg} \defnotation g \\
-	\fvars{\OTg} \defnotation \mpar{\fvars{\alpha} \cup \fvars{g} \cup \bigcup_{j \in J'} \fvars{\beta_j} \cup \bigcup_{v \in V} \fvars{\psi\mpar{v}}} \setminus V
-\end{gather*}
-\end{defi}
-The goal of the extractor \(\fvars{t}\) when \(t\) is a transition is to get variables that are only present in that transition.
-Also transition variables sets are disjoint from one transition to another.
-if we need to quantify on other variables then the quantification will be done separately.
-\begin{exi}[Enable, variable-oriented]
-The automaton drawn on the right side of Figure \ref{fig:enable} is \(\OA{\mbrc{»}}{»}{\mbrc{v}}{\mbrc{v \mapsto l}}{\mbrc{l, r}}{T}\) where transitions in \(T\) are:
-\begin{align*}
-	\OT{»}{»}{x}{\mbrc{l \mapsto x}}{v = L \wedge x \neq \delta}{\mbrc{}} &&
-	\OT{»}{»}{\tau}{\mbrc{l \mapsto \delta\mpar{x}, r \mapsto \act{acc}\mpar{y}}}{v = L \wedge x = y}{\mbrc{v \gets R}} &&
-	\OT{»}{»}{x}{\mbrc{r \mapsto x}}{v = R}{\mbrc{}}
-\end{align*}
-It is an alternative implementation of the enable operator.\footnote{It was proved FH-bisimilar to the previous one \cite{henrio:01299562}}
-The variables that are said to be local to a transition are all the unbound variables in the expressions minus the automaton variables.
-For instance \(v\) is a variable of the automaton (used in the guard).
-It is not local to the transition.
-When taking instanciated transitions, its value is not substituted with a closed term.
-For instance \nmm{\OT{»}{»}{\tau}{\mbrc{l \mapsto \tau}}{v = L \wedge \tau \neq \delta}{\mbrc{}}} is an instanciated transition generated from the second transition but not \nmm{\OT{»}{»}{\tau}{\mbrc{l \mapsto \tau}}{L = L \wedge \tau \neq \delta}{\mbrc{}}} (result of the forbidden substitution \(v \mapsto L\)).
-
-A run of this open automaton can be: The automaton in the hole \(l\) emits many actions, this synchronises with the only transition possible at that moment because \(v = L\).
-Then the automaton in hole \(l\) emits a \(\delta\mpar{t}\), this is synchronised with the action that sets \(v \gets R\) and the automata in hole \(r\) must emit a \(\act{acc}\mpar{t}\).
-Finally the automaton in the hole \(r\) emits any sequence of actions.
-
-Another run can be: The automaton in the hole \(l\) emits a sequence of non \(\delta\mpar{t}\) actions so the automaton in the hole \(r\) cannot emit a \(\act{acc}\mpar{t}\) and never runs.
-\end{exi}
-From this point open automata and open transitions are sometimes called automata and transitions for simplicity. % NEED NORMALISATION, LEFT IN CASE OF OMISSION
-
-\section{Composition of Open Automata}\label{sec:comp}
-Open automata are partially specified automata, that partiality comes mostly from the holes.
-The interpretation of a hole is an interface with another open automaton, in which we can plug an open automaton.
-The plugging operation is called composition.
-In this report, composition will only refer to filling holes, other compositions like ``parallel composition" (pure interleaving) are not tackled (but one can define an open automaton that performs the parallel composition of two others).
-The composition of open automata was already implicitly defined by the means of composition on pNets in previous work \cite{henrio:01299562} but never completely formalised on open automata.
-The definition of composition below is a direct translation of what happens with pNets composition without the need of introducing pNets.
-\begin{defi}[Composition of open automata]
-The composition of \(A_c \defobject \OAg[c]\) in the hole \(k \in J_p\) of \(A_p \defobject \OAg[p]\) gives the open automaton defined as follows.
-\begin{align*}
-	A_p\subst{A_c}{k} \defnotation & \OA{S_p \times S_c}{\mpar{s_{0p}, s_{0c}}}{V_p \uplus V_c}{\sigma_{0p} \uplus \sigma_{0c}}{J_c \uplus J_p \setminus \mbrc{k}}{T} \\
-	\text{with } T \defobject & \mset{\OT{\mpar{s_p, s_c}}{\mpar{s'_p, s'_c}}{\alpha_p}{\beta_j^{j \in J'_c \uplus J'_p \setminus \mbrc{k}}}{g_p \wedge g_c \wedge \alpha_c = \beta_k}{\psi_p \uplus \psi_c}}{\OTx{p}{}{}{p} \in T_p, \OTx{c}{}{}{c} \in T_c} \\
-	& \cup \mset{\OT{\mpar{s_p, s_c}}{\mpar{s'_p, s_c}}{\alpha_p}{\beta_j^{j \in J'_p}}{g_p}{\psi_p}}{\OTx{p}{}{}{p} \in T_p, k \notin J'_p, s_c \in S_c}
-\end{align*}
-\end{defi}
-The action emitted when \(A_c\) makes a transition is synchronised with the action of the hole \(k\) in transitions of \(A_p\) which have it as a hole action (first transition set, \(\alpha_c = \beta_k\)).
-The composition may look like a handshake, with both automata running in parallel (product of states and joint variables) however it is asymmetric because it is the first automaton that decides when the second can evolve, while the first automaton can evolve independently as soon as the hole is not involved in the open transition considered.
-\begin{exi}\label{exi:full_comp}
-\begin{figure}
-\centering
-\input{Traffic_Lights_Spec.tex}
-\caption{The specification of a traffic light system}
-\label{fig:tls}
-\end{figure}
-\begin{figure}
-\centering
-\input{Traffic_Lights_Controller.tex}
-\vrule
-\input{Traffic_Lights_Register.tex}
-\caption{On the left: An example of controller agent; On the right: An example of counter agent}
-\label{fig:tlh}
-\end{figure}
-This example is derived and adapted from a traffic light controller in a collection of examples for pNets.
-It is supposed to be a single traffic light.
-
-Figure \ref{fig:tls} shows the light controller with some synchronisation logic.
-It takes an unimplemented control circuit in the hole \(ctl\) which gives the timings and an also unimplemented counter in the hole \(cnt\) to count external \(\act{tick}\) actions.
-The three states are used to remember which colored light is on and this color can be retrieved by the environment by synchronising with the actions \(\act{onXxx}\) (Xxx is either Red, Yellow or Green) if it is not stored externally.
-
-The color switches when the counter and the control circuit agree that the time is over.
-The new time limit can be set by the control circuit and the exposed action to the exterior is a \(\tau\).
-
-The components we choose to compose in the holes are in Figure \ref{fig:tlh}.
-On the left there is the controller agent which will be composed in the hole \(ctl\).
-Its role is to decide the duration before switching the lights.
-This implementation is simply a constant time for each color; we could imagine using a more fancy controller which decides of the time depending on the traffic of each lane.
-
-On the right is the counter agent which will be composed in the hole \(cnt\).
-Its role is to get a target, then count ticks until that target is reached, then emit an action with the elapsed time and restart.
-This implementation does exactly that and forbids any extra tick.
-\begin{figure}
-\centering
-\input{Traffic_Lights_Full.tex}
-\caption{The full traffic lights system}
-\label{fig:tlf}
-\end{figure}
-The automaton on Figure \ref{fig:tlf} is a simplification of the composition of the specification on Figure \ref{fig:tls} and the agents on Figure \ref{fig:tlh}.
-The simplification was hand made because it is a hard problem as explained at the end of Section \ref{sec:comp}.
-It consisted in removing unreachable states, reducing the size of the guard and reducing the amount of variables.
-Otherwise the figure would have 36 states (\(3 \times 2 \times 6\)) but only 6 reachable from the initial configuration.
-The simplified transitions are the following (where \(n, n+1\) stands for numbers between 1 and 6, Xxx is either Red, Yellow or Green and \(\mpar{Y, X}\) is accordingly \(\mpar{Y, R}\), \(\mpar{R, G}\) or \(\mpar{G, Y}\)):
-\begin{itemize}
-\item \nmm{\OT{XnS}{X(n+1)C}{\tau}{\mbrc{}}{\top}{\mbrc{t \gets k, c \gets 0}}} which is the composition of \nmm{\OT{X}{X}{\tau}{\mbrc{ctl \mapsto \theta\mpar{x}, cnt \mapsto \act{set}\mpar{x}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{S}{C}{\act{set}\mpar{x}}{\mbrc{}}{\top}{\mbrc{t \gets x, c \gets 0}}} from the counter and \nmm{\OT{n}{n+1}{\theta\mpar{k}}{\mbrc{}}{\top}{\mbrc{}}} from the controller.
-\item \nmm{\OT{XnC}{XnC}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} which is the composition of \nmm{\OT{X}{X}{\act{tick}}{\mbrc{cnt \mapsto \act{tick}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} from the counter.
-\item \nmm{\OT{YnC}{X(n+1)S}{\act{TurnXxx}}{\mbrc{}}{c = t}{\mbrc{}}} which is the composition of \nmm{\OT{Y}{X}{\act{TurnXxx}}{\mbrc{cnt \mapsto \act{over}\mpar{x}, ctl \mapsto \delta\mpar{x}}}{\top}{\mbrc{}}} from the specification with \nmm{\OT{C}{S}{\act{over}\mpar{c}}{\mbrc{}}{c = t}{\mbrc{}}} from the counter and \nmm{\OT{n}{n+1}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} from the controller.
-\end{itemize}
-To illustrate composition, hand made simplifications and value passing, the \(\tau\) transition from the state \(R\) will be examined.
-The transition in the specification is \nmm{\OT{R}{R}{\tau}{\mbrc{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}.
-The composition can produce 12 states containing the \(R\) state, these states are in \(\mbrc{R} \times \mdbrk{1; 6} \times \mbrc{S, C}\), however only \(R1S\) and \(R2C\) are reachable so we will only consider \(\tau\) transitions from these two.
-The holes \(cnt\) and \(ctl\) are both involved in the \(\tau\) transition and filled with automata so the composed automata must synchronise with a transition.
-
-In the state \(R2C\) the composition produces 2 transitions by composition out of the \(\tau\) transition but both have a false guard; It is still interesting to look at one of them to show the product of composition without simplification.
-
-\nmm{\OT{R2C}{R3C}{\tau}{\mbrc{}}{\top \wedge \top \wedge c < t \wedge \act{set}\mpar{x} = \act{tick} \wedge \theta\mpar{x} = \delta\mpar{x_C}}{\mbrc{c \gets c + 1}}} is made with \nmm{\OT{2}{3}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} from the controller and \nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} from the counter.
-Obviously the equality of actions in the guard cannot be satisfied so the guard is false, it is equivalent to have no transition.
-We could go on to another transition but something worth explaining happened to build its guard.
-The first two \(\top\) come from the guards of the specification and the controller.
-\(c < t\) comes from the counter.
-The rest of the guard comes from the equality constraint between holes actions and automata actions.
-When composing this expression, we can see that the \(x\) variables from the specification, the controller and the counter are in conflict.
-To resolve the conflict, the conflicted variables were renamed depending on where they come from.
-
-In the state \(R1S\) the composition produces 1 transition out of the \(\tau\) transition.
-The simplified transition follows the first pattern in the transitions described before.
-Examining the composition process can illustrate how value passing work.
-The obtained guard is \(\top \wedge \top \wedge \top \wedge \theta\mpar{x} = \theta\mpar{17} \wedge \act{set}\mpar{x} = \act{set}\mpar{x_R}\) and the obtained variable assignment is \(\mbrc{t \gets x_R, c \gets 0}\).
-We can see how value passing works in the equality constraints: the only possible value of \(x\) and \(x_R\) making the guard hold is \(17\), this value has been synchronised from the controller to \(x\) then to the second occurrence of \(x\) to the distinct \(x\) of the counter.
-Note that \nmm{\OT{S}{C}{\act{set}\mpar{t}}{\mbrc{}}{\top}{\mbrc{c \gets 0}}} wouldn't have worked as a transition for the controller because \(t\) is not a transition variable, its value is fixed before the transition and cannot be set outside of the variable update, hence the use of an auxiliary variable \(x\).
-\end{exi}
-Composition is a complex process that generates big automata with complex and potentially simplifiable transitions.
-However simplification is a hard problem that is not yet automatised on open automata, so from this point the guards and transitions will always be simplified by hand without further explanation.
-\begin{prop}[Simultaneous composition]
-Let \(A_1\), \(A_2\), \(A_3\) be three open automata with respectively \(J_1\), \(J_2\) and \(J_3\) as hole names.
-We have
-\begin{align*}
-	A_1\subst{A_2}{j}\subst{A_3}{j'} & = A_1\subst{A_3}{j'}\subst{A_2}{j} & j, j' & \in J_1 \\
-	\mpar{A_1\subst{A_2}{j_1}}\subst{A_3}{j_2} & = A_1\subst{A_2\subst{A_3}{j_2}}{j_1} & \mpar{j_1, j_2} & \in J_1 \times J_2
-\end{align*}
-Where the equality is modulo isomorphism (state renaming, associativity, commutativity).
-\end{prop}
-This property is induced by the composition on open pNets.
-Intuitively it holds because the cartesian product of states, the union of sets, the union of maps and the conjunction on formulas (in the guards) are commutative and associative.
-This allows us to define the simultaneous composition \(A\mdbrk{A_j^{j \in J'}}\) as the result of any order of (sequential) composition where each \(A_j\) is composed in the hole \(j\).
-Even if an automaton is composed in two distinct holes it does not share its variables, each composition makes the cartesian product of states and a disjoint union of the variables.
-In practice, variables may have to be renamed.
-
-\section{Properties of a refinement relation for Open Automata}\label{sec:proofelts}
-We want to define a refinement relation on open automata, this refinement relation is expected to have some properties to be of any use.
-In this section we list and adapt to open automata the properties expected from a refinement relation.
-
-There are several kind of refinement relation depending on the properties we want.
-For example if we are interested in producing the same sequences of actions as another automaton we may want to use trace set inclusion as a refinement.
-The main expected properties here are the standard properties on relations and the ones related to composition.
-Because of composition, a relation as strong as simulation must be used.
-
-Informally, a simulation relating two automata means that every run of one automaton can be simulated by the other.
-Simulations are defined by relating states of automata.
-Two classical automata are called in simulation if there is a simulation relating their states.
-
-Note that in the previous paragraph there are two relations:
-The first is between states of two specific automata (\(R \subseteq S_1 \times S_2\)), the second is between automata (\(A_1 \leq A_2\)).
-Generally the second relation is implicit because its definition is always \(\exists R \subseteq S_1 \times S_2, P\mpar{R}\) with \(P\) a property on the relation on states, so only talking about \(R\) by defining \(P\) is sufficient.
-However later on in this report we will define more complex relations on automata so we clarify the distinction now.
-
-A relation of second kind will be called ``relation on automata" whereas a relation of the first kind is called ``relation on configurations" as defined below.
-In the work on FH-bisimulation \cite{henrio:01055091} such a relation \(R\) was defined as triples in \(S_1 \times S_2 \times \formulas\) where for \(\mpar{s_1, s_2} \in S_1 \times S_2\) there is a unique \(f \in \formulas\) such that \(\mpar{s_1, s_2, f} \in R\).
-This is classically the definition of a function from \(S_1 \times S_2\) to \(\formulas\) so we will define it as such.
-\begin{defi}[Relation on configurations]
-A relation on configurations of \(\OAg[1]\) and \(\OAg[2]\) is a function \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
-
-Two states \(s_1 \in S_1, s_2 \in S_2\) with their respective valuations \(\sigma_1: V_1 \to \values, \sigma_2: V_2 \to \values\) are related iff \(\sigma_1 \uplus \sigma_2 \vdash R\mpar{s_1, s_2}\).
-\end{defi}
-When relating two automata \(A_1 \mathrel{\mathcal{R}} A_2\) or their configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\), \(A_1\) will be called the implementation and \(A_2\) the specification.
-
-In this section we first give expected properties for a refinement relation on open automata, then expected properties for a relation on configurations.
-Finally a conflict between the properties is underlined and solved.
-
-\subsection{Properties of the relation on open automata}
-The important properties we consider for a relation on open automata are:
-\begin{defi} A relation \(\leq\) on open automata is
-\defitem \textbf{reflexive} iff \(\forall a, a \leq a\);
-\defitem \textbf{transitive} iff \(\forall a\, b\, c, a \leq b \wedge b \leq c \implies a \leq c\);
-\defitem \textbf{a preorder} iff it is reflexive and transitive;
-\defitem \textbf{correct w.r.t.\@ composition} iff \(\forall a\, b, a\subst{b}{j} \leq a\);
-\defitem \textbf{complete w.r.t.\@ composition} iff \(\forall a\, b, a \leq b \implies \exists c, a \cong b\subst{c}{j}\);
-\defitem \textbf{context refining for composition} iff \(\forall a\, b\, c, a \leq b \implies a\subst{c}{j} \leq b\subst{c}{j}\);
-\defitem \textbf{congruent for composition} iff \(\forall a\, b\, c, a \leq b \implies c\subst{a}{j} \leq c\subst{b}{j}\);
-\defitem \textbf{compatible with composition} iff \(\forall a\, b\, c\, d, a \leq b \wedge c \leq d \implies c\subst{a}{j} \leq d\subst{b}{j}\);
-\defitem \textbf{compatible with FH-bisimulation} iff \(\forall a\, b\, c, d, a \cong b \wedge c \cong d \wedge a \leq c \implies b \leq d\).
-\end{defi}
-Reflexivity, transitivity and preorder are classical properties on relations.
-Correctness w.r.t.\@ composition means that every composition is considered a refinement.
-This property captures the expected behaviour of a refinement relation on a compositional structure like the open automata.
-Completeness w.r.t.\@ composition means that a refinement corresponds to the left automaton being equivalent to some composition of the right automaton.
-This property is useful if we want to characterise the kind of operations that can generate any refined automaton starting from the specification.
-We won't have it because extending the definition domain of the initial valuation will be a refinement which can't be expressed with composition.
-Yet a ``completeness w.r.t.\@ some set of operations" is still a strong and interesting property.
-Context refinement is the refinement being compatible with composition of the same automaton.
-Congruence is the refinement being compatible with being composed in the same automaton.
-Compatibility with composition is the conjunction of the two latter (assuming the relation is a preorder).
-This property is required on compositional structures to be of any use in verification, proofs and for model checking.
-Finally compatibility with FH-bisimulation is the refinement not being able to distinguish two FH-bisimilar automata.
-Since FH-bisimulation is the pre-existing equivalence relation, we should not introduce an incompatible proof strategy.
-
-\subsection{Properties of the relation on configurations}
-The important properties we consider for the relation on configurations are being a pre-simulation and preventing the introduction of deadlocks.
-They are defined in the following.
-\begin{defi}[Pre-simulation]
-Let \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\).
-A relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a pre-simulation if it satisfies both
-\defitem Initial configurations are related: \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\);
-\defitem From related states, all out-transitions from \(A_1\) can be simulated in \(A_2\) and their target states are related:
-\begin{multline*}
-	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \forall \sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values, \\
-	\mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \\
-	\sigma \uplus \nu \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
-\end{multline*}
-\end{defi}
-This definition translated to open automata the classical definition of simulation \cite{10.1007/3-540-54430-5_78}.
-The last formula means that for every pair of related configurations of the automaton and every possible transitions (\(\vdash g_1\)) from the first automaton, there is a possible transition (\(\vdash g_2\)) such that the produced action matches (\(\alpha_1 = \alpha_2\)), the same holes' action (\(J'_1 \cap J'_2\)) matches (\(\beta_{1j} = \beta_{2j}\)) and the target states are related after variable update.
-% OR variableS
-Apart from holes, this is a natural extension of the notion of simulation on LTS, which is the same definition without variables nor holes nor guards.
-In FH-bisimulation, holes with the same name will receive the same open automaton when composed, and the resulting open automaton will still be equivalent.
-Here we will assume that one of the related open automata can be obtained by composing an open automaton in a hole, open automaton which can have holes itself.
-This implies that there is no relation between the related automata's holes, for instance composing \(A_i\) in \(j_i\) (\(1 \leq i \leq n\)) of \(A_0\) gives the set of holes \(\mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}\) that is neither subset nor superset of \(J_0\).
-Yet we still assume that in holes with the same name, the same open automaton will be composed.
-Hence only the holes in common have to match their actions.
-However it is not sufficient to imply properties on the relation on automata like being a preorder.
-It is only a necessary condition that we put on any relation that we call a ``simulation".
-
-In addition to the above property, we expect from a refinement relation to prevent the introduction of deadlocks.
-Deadlocks are reachable configurations from which no further transition is possible.
-They can arise unpredictably when parallelism is involved (which is the case in our composition) and they generally break the intended behaviour of a system.
-Preventing them is also a required prerequisite for the refinement to preserve any liveness property.
-\begin{defi}[Deadlock reduction, intuitive definition]\label{def:dpid}
-A relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if:
-\defitem It is a pre-simulation;
-\defitem If from related states, there is a possible transition in the specification, then there is a pair of possible matching transitions from both automata:
-\begin{multline*}
-	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \to \values, \mpar{\sigma \vdash R\mpar{s_1, s_2}} \implies \\
-	\mpar{\exists t_2 \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \vdash \fguard{t_2}} \implies \\
-	\bigsymb{\exists} \mpar{t_1, t_2} \defobject \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2}, \exists \nu: \fvars{t_1} \uplus \fvars{t_2} \to \values, \\
-	\sigma \uplus \nu \vdash g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}
-\end{multline*}
-\end{defi}
-Actually, this requirement prevents the presence of deadlocks in the first automaton if there is a related non-deadlock configuration in the second.
-The exact formulation is the contraposition of the one in the previous sentence.
-Two reasons motivated the formulation given in Definition \ref{def:dpid}:
-\begin{itemize}
-\item We require a pair of matching transitions from both automata because we do not want a transition in the implementation making a configuration not a deadlock but this transition cannot be taken from the related configuration of the specification.
-\item The alternative formulation of the property would have required the unintuitive quantification on a possibly empty set of transition to state that they are not satisfied.
-\end{itemize}
-Actually the first point is not necessary, the definition can be simplified into a less intuitive version:
-\begin{defi}[Deadlock reduction, working definition]\label{def:dpwd}
-A relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if it is a pre-simulation and it satisfies the following:
-\[ \forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \]
-\end{defi}
-The requirement here is that from any related configurations, if there is a possible transition in the second automaton (whatever the value of the free variables) then there is a possible transition in the first automaton (the existential quantifier is implicit in the notation \(\vdash\)).
-The transition are not matched because the relation on configurations is a pre-simulation and it is sufficient to ensure it as will be shown in the proof.
-Apart from the matching transitions, this is exactly the same explanation as the intuitive definition.
-The expected advantage of this formulation is that a SMT should behave better without the quantifiers.
-Indeed the big disjunctions are not quantifiers because in practice the out-transitions are finitary, and so is the expansion of the disjunction.
-\begin{lem}\label{lem:dred}
-The intuitive and working definitions of deadlock reduction are equivalent.
-\end{lem}
-Let \(R\) be a pre-simulation between \(A_1 \defobject \OA{S_1}{s_{01}}{V_1}{\sigma_{01}}{J_1}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{V_2}{\sigma_{02}}{J_2}{T_2}\).
-We want to prove:
-\[ \forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \tag{WD}\label{eq:drWD} \]
-\[ \bigsymb{\iff} \]
-\begin{multline}
-	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \forall \sigma: V_1 \uplus V_2 \to \values, \mpar{\sigma \vdash R\mpar{s_1, s_2}} \implies \\
-	\mpar{\exists t_2 \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \vdash \fguard{t_2}} \implies \\
-	\bigsymb{\exists} \mpar{t_1, t_2} \defobject \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2}, \exists \nu: \fvars{t_1} \uplus \fvars{t_2} \to \values, \\
-	\sigma \uplus \nu \vdash g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}\tag{ID}\label{eq:drID}
-\end{multline}
-\begin{proof}
-\item[\(\eqref{eq:drWD}\Rightarrow\eqref{eq:drID}\):]
-	Let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \(\sigma: V_1 \uplus V_2 \to \values\) such that:
-	\[ \sigma \vdash R\mpar{s_1, s_2} \hyp{1} \]
-	We admit the left side of the second implication in \eqref{eq:drID}:
-	\[ \exists t_2 \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \vdash \fguard{t_2} \hyp{2} \]
-	And get immediately a transition \(t_2 \in \fOT{s_2}\), a valuation \(\nu: \fvars{t_2} \to \values\) and the hypothesis:
-	\[ \sigma \uplus \nu \vdash \fguard{t_2} \hyp{2'} \]
-	\(R\) satisfies \eqref{eq:drWD} with the current value of \(\mpar{s_1, s_2}\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \nmm{\biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2}} so we have:
-	\[ \sigma \uplus \nu \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{3} \]
-	The \(\vdash\) hides an implicit \(\exists\) that we use to get values to the variables in \nmm{\biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1}} in a valuation \(\mu\).
-	The left side of the implication is proved using \hyp{1} and \hyp{2'} for the branch \(t_2\) of the disjunction.
-	The right side is a disjunction so there is a \(t_1 \in \fOT{s_1}\) such that:
-	\[ \sigma \uplus \nu \uplus \mu \vdash \fguard{t_1} \hyp{3'} \]
-	At this point we have a pair \(\mpar{t_1, t_2}\) so we may be tempted to use it to prove the goal:
-	\begin{multline}
-		\bigsymb{\exists} \OTx{2}{}{2}{2} \in \fOT{s_2}, \OTx{1}{}{1}{1} \in \fOT{s_1}, \\
-		\sigma \vdash g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_1 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \goal{1}
-	\end{multline}
-	However we cannot yet prove it because we don't know whether \(t_2\) and \(t_1\) match.
-	In order to get a \(t'_2\) matching \(t_1\) we will use the fact that \(R\) is a pre-simulation:
-	\begin{multline}
-		\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \forall \sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values, \\
-		\mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \\
-		\sigma \uplus \nu \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \hyp{0}
-	\end{multline}
-	\hyp{0} with current value of \(\mpar{s_1, s_2}\), \(t_1\) and \(\sigma \uplus \mu\) as a valuation of \(V_1 \uplus V_2 \uplus \fvars{t_1}\) gives:
-	\begin{multline}
-		\mpar{\sigma \uplus \mu \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \exists t_2 \defobject \OTx{2}{}{2}{} \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \\
-		\sigma \uplus \mu \uplus \nu \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \hyp{0'}
-	\end{multline}
-	The left part of the implication is \hyp{1} and \hyp{3'}, so we get \(t'_2 \in \fOT{s_2}\), \(\nu': \fvars{t_2} \to \values\) and:
-	\[ \sigma \uplus \mu \uplus \nu' \vdash \alpha_1 = \alpha'_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J''_2} \beta_{1j} = \beta'_{2j} \wedge g'_2 \wedge R\mpar{s'_1, s''_2}\psubst{\psi_1 \uplus \psi'_2} \hyp{4} \]
-	The witnesses for \goal{1} are \(t'_2\) and \(t_1\), and the rest is proved with a combination of \hyp{4} and \hyp{3'}.
-\item[\(\eqref{eq:drWD}\Leftarrow\eqref{eq:drID}\):]
-	Let \(\mpar{s_1, s_2} \in S_1 \times S_2\) and \nmm{\sigma: V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values}.
-	We want to prove:
-	\[ \sigma \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{2} \]
-	We can admit the left part of the implication in which the big disjunction gives us a \(t_2 \in \fOT{s_2}\) and:
-	\begin{gather}
-		\sigma \vdash R\mpar{s_1, s_2} \hyp{5} \\
-		\sigma \vdash \fguard{t_2} \hyp{6}
-	\end{gather}
-	We are left to prove:
-	\[ \sigma \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{2'} \]
-	To do that we use \eqref{eq:drID} with the current value of \(\mpar{s_1, s_2}\) and \(\sigma\), and prove the premisse of the implication with \hyp{5} to get:
-	\begin{multline}
-		\mpar{\exists t_2 \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \sigma \uplus \nu \vdash \fguard{t_2}} \implies \\
-		\bigsymb{\exists} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_1} \uplus \fvars{t_2} \to \values, \\
-		\sigma \uplus \nu \vdash g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \hyp{7}
-	\end{multline}
-	The left part of the implication is proved for \(t_2\) and \(\sigma\) (for the values covered by \(\nu\)) with \hyp{6}.
-	The right part gives \(t_1\), \(t'_2\) and \(\nu\) such that (only the interesting part of the conjunction has been extracted):
-	\[ \sigma \uplus \nu \vdash \fguard{t_1} \hyp{8} \]
-	Which proves \goal{2'} with the values of \(\nu\) for the variables of \(\fguard{t_1}\) and dummy values for the other guards.
-\end{proof}
-Unfortunately, in the general case, this property is conflicting with the properties about the relation on automata because every property involving composition would be applicable on composition introducing deadlocks.
-
-\subsection{Issue with deadlock reduction and composition}
-A way to solve the conflict between deadlock reduction and the properties involving composition is to only consider a composition that do not introduce deadlocks.
-With this new condition on validity of composition we are able to define in the next sections a refinement relation where most of the properties of interest are satisfied.
-
-Before characterising a composition which does not introduce deadlocks we need to be able to tell which states are reachable because some deadlocks are not reachable and should not be considered as being introduced.
-\begin{defi}[Reachability]
-For any open automata \(A \defobject \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is a predicate on states satisfying both
-\defitem Inital state is reachable: \(\sigma_0 \vdash \reach{A}\mpar{s_0}\)
-\defitem Reachability is preserved across transitions: \nmm{\forall t \defobject \OTg \in T, \fvars{t} \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}}
-\end{defi}
-The reachability predicate is used to characterise the reachable configurations in a run of an automaton.
-In fact the role of the predicate is to characterise potentially reachable configurations without having to characterise configurations as the result of a valid path in an automaton.
-
-To do that we impose that the initial configuration is reachable and that reachability is preserved by taking valid transitions.
-This effectively makes reachability take into account all paths, and potentially over-approximate the reachable configurations.
-The exact reachability may not be representable in the formulas, hence the need of potentially over-approximating.
-\begin{defi}[Non-locking composition, intuitive definition]
-Let \(A_i \defobject \OAg[i], 0 \leq i \leq n\).
-The composition \(A \defobject A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is non-locking if \(A\) has a reachability predicate satisfying:
-From reachable configurations, if there was a possible transition in \(A_0\) then there is a possible transition in \(A\).
-Formally for \(\OAg \defobject A\), it gives
-\begin{multline*}
-	\forall s \defobject \mpar{s'_i}_{0 \leq i \leq n} \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A}\mpar{s}} \implies \\
-	\mpar{\exists t_0 \in \fOT{s'_0}, \exists \nu_0: \fvars{t_0} \to \values, \sigma \uplus \nu_0 \vdash \fguard{t_0}} \implies \\
-	\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t}
-\end{multline*}
-\end{defi}
-As in the previous section, the definition can be simplified into a less intuitive version:
-\begin{defi}[Non-locking composition, working definition]
-\(A \defobject A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is a non-locking composition if:
-\[ \forall s \defobject \mpar{s_0, s'} \in S, V \uplus \biguplus_\subbox{t_0 \in \fOT{s_0}} \fvars{t_0} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_0 \in \fOT{s_0}} \fguard{t_0} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
-\end{defi}
-\begin{lem} The intuitive and working definition of non-locking composition are equivalent. \end{lem}
-We want to prove
-\[ \forall s \defobject \mpar{s_p, s_c} \in S, V \uplus \biguplus_\subbox{t_p \in \fOT{s_p}} \fvars{t_p} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \tag{WD}\label{eq:nlcWD} \]
-\[ \bigsymb{\iff} \]
-\begin{multline*}
-	\forall s \defobject \mpar{s_p, s_c} \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A}\mpar{s}} \implies \\
-	\mpar{\exists t_p \in \fOT{s_p}, \exists \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \vdash \fguard{t_p}} \implies \\
-	\mpar{\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t}} \tag{ID}\label{eq:nlcID}
-\end{multline*}
-\begin{proof}
-\item[\(\eqref{eq:nlcWD}\Rightarrow\eqref{eq:nlcID}\):]
-	Let \(s \defobject \mpar{s_p, s_c} \in S\) and \(\sigma \in V \to \values\) be such that:
-	\[ \sigma \vdash \reach{A}\mpar{s} \hyp{1} \]
-	We admit the left side of the second implication in \eqref{eq:nlcID}:
-	\[ \exists t_p \in \fOT{s_p}, \exists \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \vdash \fguard{t_p} \hyp{2} \]
-	We get immediately a transition \(t_p \in \fOT{s_p}\), a valuation \(\nu: \fvars{t_p} \to \values\) and the hypothesis:
-	\[ \sigma \uplus \nu \vdash \fguard{t_p} \hyp{2'} \]
-	\(\reach{A}\) satisfies \eqref{eq:nlcWD} with the current value of \(s\) and \(\sigma \uplus \nu\) completed with dummy values for the other variables of \nmm{\biguplus_\subbox{t_p \in \fOT{s_p}} \fvars{t_p}} so we have:
-	\[ \sigma \uplus \nu \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{3} \]
-	The \(\vdash\) hides an implicit \(\exists\) that we use to get \nmm{\mu: \biguplus_\subbox{t \in \fOT{s}} \fvars{t} \to \values}.
-	The left side of the implication is proved using \hyp{1} and \hyp{2'} for the branch \(t_p\) of the disjunction.
-	The right side is a big disjunction that gives us \(t \in \fOT{s}\) such that:
-	\[ \sigma \uplus \nu \uplus \mu \vdash \fguard{t} \hyp{3'} \]
-	At this point we have a \(t\) which is composed of a transition in \(A_p\) and one in \(A_c\) so unlike Lemma \ref{lem:dred} we do not need to check that two transitions matches.
-	The current goal is:
-	\[ \exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t} \]
-	Which is proved on \(t\) with valuation \(\mu\) by \hyp{3'}.
-\item[\(\eqref{eq:nlcWD}\Leftarrow\eqref{eq:nlcID}\):]
-	Let \(s \defobject \mpar{s_p, s_c} \in S\), \nmm{\sigma: V \uplus \biguplus_\subbox{t_p \in \fOT{s_p}} \fvars{t_p} \to \values}.
-	We want to prove:
-	\[ \sigma \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \goal{1} \]
-	We can admit the left part of the implication in which the big disjunction gives us \(t_p \in \fOT{s_p}\) and:\\
-	\begin{gather}
-		\sigma \vdash \reach{A}\mpar{s} \hyp{4} \\
-		\sigma \vdash \fguard{t_p} \hyp{5}
-	\end{gather}
-	We are left to prove:
-	\[ \sigma \vdash \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \goal{1'} \]
-	To do that we use \eqref{eq:nlcID} with the current value of \(s\) and \(\sigma\), and prove the premisse of the implication with \hyp{4} to get:
-	\begin{multline}
-		\mpar{\exists t_p \in \fOT{s_p}, \exists \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \vdash \fguard{t_p}} \implies \\
-		\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t} \hyp{6}
-	\end{multline}
-	The left part of the implication is proved for \(t_p\) and \(\sigma\) (for the values covered by \(\nu\)) with \hyp{5}.
-	The right part gives \(t\) and \(\nu\) such that:
-	\[ \sigma \uplus \nu \vdash \fguard{t} \hyp{7} \]
-	Which proves \goal{1'} with the values of \(\nu\) for the variables of \(\fguard{t}\) and dummy values for the other guards.
-\end{proof}
-\begin{exi}[Deadlocks introduced by composition]
-This example reuses the counter introduced in Figure \ref{fig:tlh}.
-The behaviour of the counter is to count external \(\act{tick}\) actions up to the amount set by action \(\act{set}\mpar{x}\) then to notify the environment that this amount of time elapsed.
-In the traffic light example the clock is not specified, we will introduce deadlocks using a wisely chosen clock specification.
-However the full traffic light will not be used in order to simplify the example, only the counter will be.
-\begin{figure}
-\input{randomtick_clock.tex}
-\vrule
-\input{register_anytick.tex}
-\caption{On the left: A clock which imposes a tick; On the right: A modified version of the counter at figure \ref{fig:tlh}}
-\label{fig:anytick}
-\end{figure}
-The clock on the left side of Figure \ref{fig:anytick} transmits the actions of its hole unchanged until the clock imposes a \(\act{tick}\) on its hole.
-This can model a physical clock, because physical time ticks cannot be delayed.
-
-If the hole cannot handle a \(\act{tick}\) at any time then there is a deadlock, which is the case with our counter.
-The composition of this clock with the counter is given on the left of Figure \ref{fig:deadlock}.
-\begin{figure}
-\input{Composition_deadlock.tex}
-\vrule
-\input{Composition_nolock.tex}
-\caption{On the left: Deadlocks introduced by composition; On the right: No deadlock introduced by composition}
-\label{fig:deadlock}
-\end{figure}
-There are two deadlocks:
-The first is in the state \(1S\), which corresponds to the clock trying to impose a tick when the counter is not set.
-The second is in the state \(1C\), which corresponds to the clock trying to impose a tick when the counter has reached the amount previously set, but not has not yet reported it to the environment.
-These deadlocks could have been in the specification in which case they were intended, but it is not the case here.
-
-The counter on the right of Figure \ref{fig:anytick} is a modification to accept ticks at in any state.
-Composing this modified counter gives the automaton on the right of Figure \ref{fig:deadlock} which has no deadlocks.
-
-We should successfully characterise the second composition as non-locking but fail for the first.
-\begin{itemize}
-\item In the state \(0S\) any valuation is reachable (no initial valuation).
-	In both automata the transition \nmm{\OT{0S}{1S}{\tau}{\mbrc{}}{\top}{\mbrc{}}} has a true guard, hence the first branch of the disjunction holds.
-\item In the state \(0C\), for the left automaton, valuations where \(t \geq c \geq 0 \vee \mpar{t < 0 \wedge c = 0}\) are reachable; for the right automaton, valuations where \(c \geq 0\) are reachable.
-	For all these valuations the transition \nmm{\OT{0C}{1C}{\tau}{\mbrc{}}{\top}{\mbrc{}}} has a true guard, hence the first branch of the disjunction holds.
-\item In the state \(1C\), the same valuations as the ones reachable in \(0C\) are also reachable.
-	In the right automaton the transition \nmm{\OT{1C}{0C}{\act{tick}}{\mbrc{}}{\top}{\mbrc{c \gets c + 1}}} has a true guard.
-	In the left automaton the transition \nmm{\OT{1C}{0C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} covers the cases where \(c < t\).
-	For the other cases (\(c = t \vee t \leq 0 \mbrk{\leq c}\)) there are no transition with a true guard, and in the clock the transition same transition as for the state \(1S\) has a true guard, hence the composition is not non-locking.
-\item In the state \(1S\) any valuation is reachable.
-	In the left automaton, no transition is possible, and in the parent automaton \nmm{\OT{1}{0}{\act{tick}}{\mbrc{H \mapsto \act{tick}}}{\top}{\mbrc{}}} had a true guard, so the composition is not a non-locking composition (we already know it at this point).
-	In the right automaton, \nmm{\OT{1S}{0S}{\act{tick}}{\mbrc{}}{\top}{\mbrc{}}} has a true guard.
-\end{itemize}
-The left automaton indeed fails at being the result of a non-locking composition where the right automaton passes.
-
-One more thing worth noting is that for the left automaton, in the state \(1C\) with a valuation such that \(t < 0\), the counter agent is in a deadlock state.
-We could have defined the non-locking composition so that this is considered as an intended deadlock, making the requirement symmetric.
-However the the semantics of composition in a hole is asymmetric and the considered specification -as in the deadlock reduction- is the parent automaton.
-\end{exi}
-This new definition of composition can replace the standard composition.
-We may think that if the simultaneous composition is non-locking, then for every composition order, each composition step is non-locking.
-Unfortunately it is not true.
-This happens because in an intermediate composition step, a state can become a deadlock, but in a further composition step it would become unreachable.
-% However the opposite way is true: % Would need a proof, non-trivial
-% If there is an order of composition where every composition is non-locking then the last composition is non-locking, last composition resulting in the same automaton as the simultaneous composition.
-% So the condition is better checked after the simultaneous composition or the last individual composition.
-\begin{exi}
-\begin{figure}
-\centering
-\input{file_sync.tex}
-\caption{A made-up protocol for file synchronisation}
-\label{fig:pnls}
-\end{figure}
-The automaton on Figure \ref{fig:pnls} is a sample protocol for file synchronisation.
-The two holes are \(net\) a process to manage network communications, and \(hash\) a process to check files integrity.
-The state \(i\) is the initial state.
-In that state we want to synchronise the files before working, or work on the local version as a fallback.
-If the preferred version is the remote one, we go in state \(d1\) asking the network manager to fetch the latest version, then ask the integrity checker to validate the files.
-If the preferred version is the local one, we go in state \(d2\) asking for the integrity checker to validate the local files, then ask the network manager to push them.
-In fallback we use the local version.
-
-We can plug an inactive process for the network manager and the file integrity checker by composing a deadlock automaton in their holes, but always both at the same time.
-The reason for that is the simultaneous composition is non-locking, but any individual composition is locking because either the state \(d1\) or \(d2\) (depending on the order) is reachable and becomes a deadlock.
-\end{exi}
-From this point and when checking the refinement properties, composition will only refer to non-locking composition.
-
-\section{Refinement relations in restricted cases}\label{sec:prelref}
-With all these properties explained, we can look at some concrete refinement relations.
-The main goal of this section is to explain the different aspects of refinement in restricted cases so that they are not all introduced at once in the real refinement relation.
-In particular if we have a family of open automata \(A_i \defobject \OAg[i]\), \(0 \leq i \leq n\), let \(A \defobject A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\).
-Recall that there is no relation between the holes of \(A\) and \(A_0\) because \(\mpar{\biguplus_{0 \leq i \leq n} J_i} \setminus \mset{j_i}{1 \leq i \leq n}\) is neither subset nor superset of \(J_0\).
-So looking at restricted cases where holes are related in a specific manner can help understanding the general case.
-Hopefully the intermediate refinement relation introduced can be used as simpler (and less expensive to compute) versions of the real refinement relation in the case the manipulated automata respect some constraints.
-
-We restrict the holes of the related automata so that we can explain the different refinements without their interactions.
-In the following definition, \(\triangle \in \mbrc{\subseteq, =, \supseteq}\).
-\begin{defi}[Hole-\(\triangle\) simulation]
-For two open automata \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\triangle\) simulation of \(A_1\) by \(A_2\) if:
-\item[1)] \(J_1 \triangle J_2\)
-\item[2)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
-\item[3)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)\vspace{-8pt}
-\noindent\begin{multline*}
-	\mpar{\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
-		\quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
-		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}}
-	\end{array}} \\
-	\wedge \mpar{V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
-\end{multline*}
-\end{defi}
-The third item of the definition has two parts:
-The first part is the main requirement, a stronger version of the pre-simulation requirement so that it better fits SMT.
-Instead of matching an instanciated transition to another instanciated transition as in the pre-simulation definition, we match an open transition to a family of covering open-transitions.
-The second part is directly the deadlock reduction requirement.
-
-The hole-equal simulation is applicable when the related automata have the same holes.
-It is designed to capture all the refinements other than composition: Duplicating and merging states and transitions, changing variables, removing transitions, adding requirements to guards, specifying more initial variables, and many more.
-
-The hole-subset simulation is applicable when the simulated automaton has less holes.
-It is designed to have composition correctness when the composed automata have no holes.
-
-The hole-superset simulation is applicable when the simulated automaton has more holes.
-It is designed to capture the addition of holes involved in transitions, which will indirectly add requirements to transitions when the new holes will be composed.
-It is also an attempt at giving a meaning to the new holes when composing with any open automata.
-However it does not capture the removal of holes because other issues arise when trying to both add and remove holes.
-\begin{exi}[Example of hole-equal simulation]
-\begin{figure}
-\centering
-\input{parallel_comp.tex}
-\vrule
-\input{n_control_switch.tex}
-\caption{On the left: Parallel composition operator; On the right: n control switches automaton}
-\label{fig:hisim}
-\end{figure}
-Figure \ref{fig:hisim} introduces two related open automata with same holes \(\mbrc{l, r}\).
-The automaton on the left is a parallel composition: any hole can perform actions at any time, the actions are passed unmodified and no synchronisation is performed.
-The automaton on the right is a sequential composition with \(n\) control switches: a hole performs a sequence of actions then the other does, there are \(n\) sequences of a single automaton doing actions without the other performing some.
-
-Intuitively the right automaton is a refinement of the left automaton because the left automaton is what happens when there was no bound \(n\) in the right automaton.
-\[ R \defobject \mbrc{\mpar{l, ||} \mapsto \top, \mpar{r, ||} \mapsto \top} \]
-\(R\) is a hole-identical simulation of \(n\) control switches by parallel composition.
-There are enough examples of proofs of refinement in this report for the reader to be able to prove it as an exercise.
-\end{exi}
-\begin{exi}[Example of hole-subset simulation]
-The automata of Example \ref{exi:full_comp} can be reused here.
-The automaton on Figure \ref{fig:tlf} is a refinement of the one on Figure \ref{fig:tls} by limited composition correctness (Proposition \ref{prop:cc'} below).
-
-It is a simplified version of the motivation for making a refinement relation, which is the traffic light system in an article about weak-bisimulation \cite{wang:03126313}.
-It had to be modified because here the simulation is a strong-simulation (no silent actions).
-\end{exi}
-\begin{exi}[Example of hole-superset simulation]
-\begin{figure}
-\centering
-\input{Vending_machine.tex}
-\vspace{3pt}
-\hrule
-\vspace{3pt}
-\input{Open_vending_machine.tex}
-\caption{On the top: Vending machine; On the bottom: Open vending machine}
-\label{fig:ovm}
-\end{figure}
-Figure \ref{fig:ovm} introduces two related open automata with same states and transitions except for hole actions.
-Both automata are vending machine: Money is introduced while in state \(I\), accumulating in the money variable \(m\), when there are enough money a coffee or a tea can be ordered by taking the transitions to the states \(C\) or \(T\) and money is decreased, then the drink is served by taking the transition back to state \(I\).
-The holes added in the open version on the bottom are \(mon\) a hole which task is to verify the money inserted (coin vary depending on the country for instance) and \(serv\) which task is to serve the drink and report the exact amount served.
-
-The automaton on the bottom is a refinement of the automaton on the top using hole-superset simulation.
-The relation on states is the same as the one for reflexivity.
-Intuitively the automaton on the bottom binds some variables to action produced by the holes, the automaton is no more free to take a transition some hole is not able to perform.
-For instance if the automaton in the hole \(mon\) can only perform \(\act{credit}\mpar{100}\) then after the composition, the automaton on the bottom should be a refinement of the one on the top.
-Actually after such a composition it is still in hole-superset simulation with the top automaton by Proposition \ref{prop:cc'}.
-\end{exi}
-\begin{thm} A hole-\(\triangle\) simulation is a pre-simulation. \end{thm}
-\begin{proof}
-Let \(R\) be a relation on configurations.
-The condition \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\) is in both definitions and the deadlock reduction requirement will not be used so proving the following is sufficient:
-\begin{multline}
-	\forall \mpar{s_1, s_2} \in S_1 \times S_2, \\
-	\mpar{\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
-		\quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
-		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}}
-	\end{array}} \hyp{0}
-\end{multline}
-\[ \bigsymb{\implies} \]\vspace{-1cm}
-\begin{multline}
-	\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \forall \sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values, \\
-	\mpar{\sigma \vdash R\mpar{s_1, s_2} \wedge g_1} \implies \bigsymb{\exists} t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \\
-	\sigma \uplus \nu \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \goal{0}
-\end{multline}
-Let \(\mpar{s_1, s_2} \in S_1 \times S_2\), \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}} and \(\sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values\) be such that
-\[ \sigma \vdash R\mpar{s_1, s_2} \wedge g_1 \hyp{1} \]
-In order to get the transition required to prove
-\begin{multline}
-	\bigsymb{\exists} t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \exists \nu: \fvars{t_2} \to \values, \\
-	\sigma \uplus \nu \vdash \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \wedge g_2 \wedge R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2} \goal{0'}
-\end{multline}
-we use the hypothesis \hyp{0} with the transition \(t_1\) and get a family of transitions
-\[ \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X} \]
-such that the two following properties hold
-\begin{gather}
-	\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2 \hyp{2} \\
-	V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-		\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
-		\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-	\end{array}} \hyp{3}
-\end{gather}
-\hyp{3} holds for every values of the variables in \(V_1 \uplus V_2 \uplus \fvars{t_1}\) so in particular with the ones given by \(\sigma\).
-We gather the variables of the implicit \(\exists\) in a valuation \nmm{\nu: \biguplus_{x \in X} \fvars{t_{2x}} \to \values}.
-\[ \sigma \uplus \nu \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \bigvee_{x \in X} \mpar{\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \wedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \hyp{3'} \]
-The left side of the implication is proved by \hyp{1}, and for the right side we get \(x \in X\) such that
-\[ \sigma \uplus \nu \vdash \alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \wedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \hyp{4} \]
-We have \(J'_{2x} \cap J_1 = J'_{2x} \cap J'_1\) in \hyp{4}:
-\begin{align*}
-	J'_{2x} \cap J_1 & \subseteq J'_{2x} \tag{1} \\
-	J'_{2x} \cap J_1 & = J'_1 \cap J_2 & \text{by \hyp{2}} \\
-	& \subseteq J'_1 \tag{2} \\
-	J'_{2x} \cap J_1 & \subseteq J'_{2x} \cap J'_1 & \text{by (1) and (2)} \tag{3} \\
-	J'_{2x} \cap J'_1 & \subseteq J'_{2x} \cap J_1 & \text{by } J'_1 \subseteq J_1 \tag{4} \\
-	J'_{2x} \cap J_1 & = J'_{2x} \cap J'_1 & \text{by (3) and (4)}
-\end{align*}
-So we can prove \goal{0'} for the transition \(t_{2x}\) and the valuation \(\nu\) using \hyp{4}.
-\end{proof}
-\begin{thm} The hole-\(\triangle\) simulation on automata is a preorder. \end{thm}
-\begin{proofsketch}
-The idea for reflexivity is that the related automata are always in the same configuration.
-\[ R \defobject \mpar{s, s'} \mapsto \choice{\bigwedge_{v \in V} v_1 = v_2 & \text{if } s = s'\\ \bot & \text{otherwise}} \]
-Where \(v_x\) is the renaming to distinguish conflicting automaton variables.
-\(R\) is a witness of the reflexivity, the proof is mainly the same as several of the following ones so it will be omitted.
-\end{proofsketch}
-For transitivity we need to introduce three open automata.
-Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\) be open automata.
-Let \(R_{12}\) be a hole-\(\triangle\) simulation of \(A_1\) by \(A_2\) and \(R_{23}\) of \(A_2\) by \(A_3\).
-The idea for \(R\) is that there exists a state \(s_2 \in S_2\) and values for \(V_2\) such that \(R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3}\).
-However we cannot talk about states in formulas.
-The solution is to expand the existential quantifier on states as we did in deadlock reduction, which is possible because states are finite.
-\[ R \defobject \mpar{s_1, s_3} \mapsto \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \]
-We want to prove that \(R\) is a hole-\(\triangle\) simulation of \(A_1\) by \(A_3\).
-\begin{proof}
-\item[1)] By transitivity of \(\triangle\), \(J_1 \triangle J_3\)
-\item[2)] We prove that initial configurations are related using \(\sigma_{02}\) as the values of the variables in \(V_2\), and \(s_{02}\) to choose the branch of the disjunction.
-\begin{align*}
-	\sigma_{01} \uplus \sigma_{03} \vdash R\mpar{s_{01}, s_{03}} \iff & \sigma_{01} \uplus \sigma_{03} \vdash \exists V_2, \bigvee_\subbox{s_2 \in S_2} R_{12}\mpar{s_{01}, s_2} \wedge R_{23}\mpar{s_2, s_{03}} \\
-	\impliedby & \sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03} \vdash R_{12}\mpar{s_{01}, s_{02}} \wedge R_{23}\mpar{s_{02}, s_{03}} \\
-	\impliedby & \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar{\sigma_{02} \uplus \sigma_{03} \vdash R_{23}\mpar{s_{02}, s_{03}}}
-\end{align*}
-\item[3)] Let \(\mpar{s_1, s_3} \in S_1 \times S_3\), we want to prove both
-	\begin{align*}
-		& \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{3x} \defobject \OTx{3}{x}{3x}{3x} \in \fOT{s_3}}^{x \in X}, \\
-		& \mpar{\forall x \in X, J'_{3x} \cap J_1 = J'_1 \cap J_3} \\[-10pt]
-		& \wedge V_1 \uplus V_3 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_3} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_1 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x} \cap J_1} \beta_{1j} = \beta_{3xj} \\[12pt]
-			\nwedge g_{3x} \wedge R\mpar{s'_1, s'_{3x}}\psubst{\psi_1 \uplus \psi_{3x}}
-		\end{array}} \goal{0}
-	\end{align*}
-	\[ V_1 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash R\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{1} \]
-\item[\goal{0}:] Let \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}}.
-	For every \(s_2 \in S_2\) we have the hypotheses on \(R_{12}\) and \(R_{23}\):
-	\begin{gather}
-		\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{s2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
-		\quad \mpar{\forall x \in X, J'_{s2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
-		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R_{12}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{s2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}}
-		\end{array} \hyp{0} \\
-		\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \bigsymb{\exists} \mpar{t_{3x} \defobject \OTx{3}{x}{3x}{3x} \in \fOT{s_3}}^{x \in X}, \\
-		\quad \mpar{\forall x \in X, J'_{3x} \cap J_2 = J'_2 \cap J_3} \\[-10pt]
-		\nwedge V_2 \uplus V_3 \uplus \fvars{t_{s2}} \vdash R_{23}\mpar{s_2, s_3} \wedge g_2 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-			\alpha_2 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x} \cap J_2} \beta_{2j} = \beta_{3xj} \\[12pt]
-			\nwedge g_{3x} \wedge R_{23}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
-		\end{array}}
-		\end{array} \hyp{1}
-	\end{gather}
-	We use hypothesis \hyp{0} with \(t_1\) for every \(s_2 \in S_2\) to get
-	\begin{gather*}
-		\mpar{t_{s2x} \defobject \OT{s_2}{s'_{s2x}}{\alpha_{s2x}}{\beta_{s2xj}^{j \in J'_{s2x}}}{g_{s2x}}{\psi_{s2x}} \in \fOT{s_2}}^{x \in X_{s2}} \\
-		\forall x \in X, J'_{s2x} \cap J_1 = J'_1 \cap J_2 \hyp{0'} \\
-		V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R_{12}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X_{s2}} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_1 = \alpha_{s2x} \wedge \bigwedge_\subbox{j \in J'_{s2x} \cap J_1} \beta_{1j} = \beta_{s2xj} \\[12pt]
-			\nwedge g_{s2x} \wedge R_{12}\mpar{s'_1, s'_{s2x}}\psubst{\psi_1 \uplus \psi_{s2x}}
-		\end{array}} \hyp{0"}
-	\end{gather*}
-	Then use \hyp{1} with every \(t_{s2x}\) to get
-	\begin{gather*}
-		Z_{s2x} \defobject \mbrc{s_2} \times \mbrc{x} \times Y_{s2x} \\
-		\mpar{t_{3z} \defobject \OTx{3}{z}{3z}{3z} \in \fOT{s_3}}^{z \in Z_{s2x}} \\
-		\forall z \in Z_{s2x}, J'_{3z} \cap J_2 = J'_{s2x} \cap J_3 \hyp{1x} \\
-		V_2 \uplus V_3 \uplus \fvars{t_{s2x}} \vdash R_{23}\mpar{s_2, s_3} \wedge g_{s2x} \implies \operatorname*{\bigsymb{\bigvee}}_\subbox{z \in Z_{s2x}} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{s2x} = \alpha_{3z} \wedge \bigwedge_\subbox{j \in J'_{3z} \cap J_2} \beta_{s2xj} = \beta_{3zj} \\[12pt]
-			\nwedge g_{3z} \wedge R_{23}\mpar{s'_{s2x}, s'_{3z}}\psubst{\psi_{s2x} \uplus \psi_{3z}}
-		\end{array}} \hyp{1x'}
-	\end{gather*}
-	We pose \nmm{Z \defobject \biguplus_{s_2 \in S_2} \biguplus_{x \in X_{s2}} Z_{s2x}}.
-	We will prove \goal{0} for the family \(t_{3z}^{z \in Z}\).
-	The new goals are:
-	\begin{gather}
-		\forall z \in Z, J'_{3z} \cap J_1 = J'_1 \cap J_3 \goal{0'} \\
-		V_1 \uplus V_3 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_3} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{z \in Z} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_1 = \alpha_{3z} \wedge \bigwedge_\subbox{j \in J'_{3z} \cap J_1} \beta_{1j} = \beta_{3zj} \\[12pt]
-			\nwedge g_{3z} \wedge R\mpar{s'_1, s'_{3z}}\psubst{\psi_1 \uplus \psi_{3z}}
-		\end{array}} \goal{2}
-	\end{gather}
-\item[\goal{0'}:] By case on \(\triangle\):
-	\begin{itemize}
-	\item Let \(\triangle\) be \(\subseteq\).
-		\begin{align*}
-		J'_{3z} \cap J_1 & \subseteq J'_{3z} \cap J_2 & \text{by } & J_1 \subseteq J_2 \\
-			& \subseteq J'_{2x} \cap J_3 & \text{by } & \text{\hyp{1x}} \hyp{2} \\
-			& \subseteq J'_{2x} \cap J_3 \cap J_1 & \text{by } & J'_{3z} \cap J_1 \subseteq J_1 \\
-			& \subseteq J'_{2x} \cap J_1 && \\
-			& \subseteq J'_1 \cap J_2 & \text{by } & \text{\hyp{0'}} \hyp{2'} \\
-			& \subseteq J'_1 \cap J_3 & \text{by } & J_2 \subseteq J_3
-		\end{align*}
-		\begin{align*}
-		J'_1 \cap J_3 & = J'_1 = J'_1 \cap J_2 & \text{by } & J'_1 \subseteq J_1 \subseteq J_2 \subseteq J_3 \\
-			& = J'_{2x} \cap J_1 & \text{by } & \text{\hyp{0'}} \\
-			& \subseteq J'_{2x} \cap J_3 & \text{by } & J_1 \subseteq J_3 \\
-			& \subseteq J'_{3z} \cap J_2 & \text{by } & \text{\hyp{1x}} \\
-			& \subseteq J'_{3z} \cap J_2 \cap J_1 & \text{by } & J'_1 \subseteq J_1 \\
-			& \subseteq J'_{3z} \cap J_1 &&
-		\end{align*}
-	\item Let \(\triangle\) be \(\supseteq\).
-		\begin{align*}
-		J'_1 \cap J_3 & \subseteq J'_1 \cap J_2 & \text{by } & J_3 \supseteq J_2 \\
-			& \subseteq J'_{2x} \cap J_1 & \text{by } & \text{\hyp{0'}} \\
-			& \subseteq J'_{2x} \cap J_1 \cap J_3 & \text{by } & J'_1 \cap J_3 \subseteq J_3 \\
-			& \subseteq J'_{2x} \cap J_3 && \\
-			& \subseteq J'_{3z} \cap J_2 & \text{by } & \text{\hyp{1x}} \\
-			& \subseteq J'_{3z} \cap J_1 & \text{by } & J_1 \supseteq J_2
-		\end{align*}
-		\begin{align*}
-		J'_{3z} \cap J_1 & = J'_{3z} = J'_{3z} \cap J_2 & \text{by } & J_1 \supseteq J_2 \supseteq J_3 \supseteq J'_{3z} \\
-			& = J'_{2x} \cap J_3 & \text{by } & \text{\hyp{1x}} \hyp{3} \\
-			& \subseteq J'_{2x} \cap J_1 & \text{by } & J_1 \supseteq J_3 \\
-			& \subseteq J'_1 \cap J_2 & \text{by } & \text{\hyp{0'}} \hyp{3'} \\
-			& \subseteq J'_1 \cap J_2 \cap J_3 & \text{by } & J'_{3z} \subseteq J_3 \\
-			& \subseteq J'_1 \cap J_3 &&
-		\end{align*}
-	\item Let \(\triangle\) be \(=\).
-		We use either one of the proof for the two above cases so \goal{0'} holds.
-	\end{itemize}
-\item[\goal{2}:] Let \(\sigma_1: V_1 \uplus \fvars{t_1} \to \values\) and \(\sigma_3: V_3 \to \values\).
-	We use dummy values for variables in \nmm{\biguplus_\subbox{z \in Z} \fvars{t_{3z}}} to get the left side of this implication as an hypothesis (independent from these values):
-	\[ \sigma_1 \uplus \sigma_3 \vdash R\mpar{s_1, s_3} \wedge g_1 \hyp{4} \]
-	Hypothesis immediately broken down into
-	\begin{gather*}
-		\sigma_2: V_2 \to \values \quad s_2 \in S_2 \\
-		\sigma_1 \uplus \sigma_2 \uplus \sigma_3 \vdash R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \hyp{4'} \\
-		\sigma_1 \vdash g_1 \hyp{4"}
-	\end{gather*}
-	We can use immediately \hyp{0"} with valuation \(\sigma_1 \uplus \sigma_2\) to get \nmm{\nu_2: \biguplus_{x \in X} \fvars{t_{2x}} \to \values}.
-	The left side of the implication is proved with the right side of \hyp{4'} and \hyp{4"}, so we get \(x \in X_{s2}\) and the hypotheses
-	\begin{align}
-		\sigma_1 \uplus \sigma_2 \uplus \nu_2 & \vdash \alpha_1 = \alpha_{s2x} \hyp{5a} \\
-		\sigma_1 \uplus \sigma_2 \uplus \nu_2 & \vdash \bigwedge_\subbox{j \in J'_1 \cap J_{s2x}} \beta_{1j} = \beta_{s2xj} \hyp{5b} \\
-		\sigma_2 \uplus \nu_2 & \vdash g_{s2x} \hyp{5c} \\
-		\sigma_1 \uplus \sigma_2 \uplus \nu_2 & \vdash R\mpar{s'_1, s'_{s2x}}\psubst{\psi_1 \uplus \psi_{s2x}} \hyp{5d}
-	\end{align}
-	We can now use \hyp{1x'} with valuation \(\sigma_2 \uplus \nu_2 \uplus \sigma_3\) to get \nmm{\nu_3: \biguplus_\subbox{Z \in Z_{s2x}} \fvars{t_{3z}} \to \values}.
-	The left side of the implication is proved with the left side of \hyp{4'} and \hyp{4"}, so we get \(z \in Z_{s2x}\) and the hypotheses
-	\begin{align}
-		\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3 & \vdash \alpha_{s2x} = \alpha_{3z} \hyp{6a} \\
-		\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3 & \vdash \bigwedge_\subbox{j \in J'_{s2x} \cap J_{3z}} \beta_{s2xj} = \beta_{3zj} \hyp{6b} \\
-		\sigma_3 \uplus \nu_3 & \vdash g_{3z} \hyp{6c} \\
-		\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3 & \vdash R\mpar{s'_{s2x}, s'_{3z}}\psubst{\psi_{s2x} \uplus \psi_{3z}} \hyp{6d}
-	\end{align}
-	In order to progress on \goal{2} we give valuation \(\nu_3\) for the implicit \(\exists\), admit the left side of the implication and choose to prove the branch \(z\):
-	\begin{align}
-		\sigma_1 \uplus \sigma_3 \uplus \nu_3 & \vdash \alpha_1 = \alpha_{3z} \goal{2a} \\
-		\sigma_1 \uplus \sigma_3 \uplus \nu_3 & \vdash \bigwedge_\subbox{j \in J'_{3z} \cap J_1} \beta_{1j} = \beta_{3zj} \goal{2b} \\
-		\sigma_3 \uplus \nu_3 & \vdash g_{3z} \goal{2c} \\
-		\sigma_1 \uplus \sigma_3 \uplus \nu_3 &\vdash R\mpar{s'_1, s'_{3z}}\psubst{\psi_1 \uplus \psi_{3z}} \goal{2d}
-	\end{align}
-	\goal{2a} is proved by transitivity using \hyp{5a} and \hyp{5a}.
-	\goal{2b} is proved using \hyp{5b} and \hyp{6b}, but depending on \(\triangle\) the equality are obtained for the interesting values \(j\) using either \hyp{2} and \hyp{2'} or \hyp{3} and \hyp{3'}.
-	\goal{2c} is exactly \hyp{6c}.
-	We prove \goal{2d} with valuation \(\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}\) for the branch \(s_2\):
-	\begin{align*}
-		& \sigma_1 \uplus \sigma_3 \uplus \nu_3 \vdash R\mpar{s'_1, s'_{3z}}\psubst{\psi_1 \uplus \psi_{3z}} \\
-		\iff & \mpar{R_{12}\mpar{s'_1, s'_2} \wedge R_{23}\mpar{s'_2, s'_3}}\psubst{\psi_1 \uplus \psi_{3z}}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_1 \uplus \sigma_3 \uplus \nu_3} \\
-		\iff & R_{12}\mpar{s'_1, s'_2}\psubst{\psi_1}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_1} \wedge R_{23}\mpar{s'_2, s'_3}\psubst{\psi_{3z}}\psubst{\psi_{s2x}\psubst{\sigma_2 \uplus \nu_2}}\psubst{\sigma_3 \uplus \nu_3} \\
-		\iff & R_{12}\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_{s2x}}\psubst{\sigma_2 \uplus \nu_2 \uplus \sigma_1} \wedge R_{23}\mpar{s'_2, s'_3}\psubst{\psi_{3z} \uplus \psi_{s2x}}\psubst{\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3} \\
-		\iff & \mpar{\sigma_2 \uplus \nu_2 \uplus \sigma_1 \vdash R_{12}\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_{s2x}}} \wedge \mpar{\sigma_2 \uplus \nu_2 \uplus \sigma_3 \uplus \nu_3 \vdash R_{23}\mpar{s'_2, s'_3}\psubst{\psi_{3z} \uplus \psi_{s2x}}}
-	\end{align*}
-	Which is proved by \hyp{5d} and \hyp{6d}.
-	The manipulations of substitutions are possible because their definition domain are disjoint; more details are available in the proof for transitivity of FH-bisimulation \cite{2007.10770}.
-\item[\goal{1}:] Let \(\sigma_1: V_1 \to \values\) and \nmm{\sigma_3: V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \to \values}.
-	We have the hypotheses on \(R_{12}\) and \(R_{23}\) for the states \(s_1\) and \(s_3\), then the current goal:
-	\begin{gather}
-		\forall s_2 \in S_2, V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{7} \\
-		\forall s_2 \in S_2, V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash R_{23}\mpar{s_2, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{8} \\
-		\sigma_1 \uplus \sigma_3 \vdash R\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \goal{1'}
-	\end{gather}
-	We use dummy values for variables in \nmm{\biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1}} to get the left side of this implication as an hypothesis (independent from these values):
-	\[ \sigma_1 \uplus \sigma_3 \vdash R\mpar{s_1, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \hyp{9} \]
-	Hypothesis that we immediately break down into:
-	\begin{gather*}
-		\sigma_2: V_2 \to \values \quad s_2 \in S_2 \\
-		\sigma_1 \uplus \sigma_2 \uplus \sigma_3 \vdash R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \hyp{9'} \\
-		\sigma_1 \uplus \sigma_3 \vdash \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \hyp{9"}
-	\end{gather*}
-	We can use \hyp{8} with state \(s_2\) and valuation \(\sigma_2 \uplus \sigma_3\) to get \nmm{\nu_2: \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values}.
-	The left side of the implication is proved with the right side of \hyp{9'} and \hyp{9"}, so we get
-	\[ \sigma_3 \uplus \nu_2 \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{8'} \]
-	We can now use \hyp{7} with state \(s_2\) and valuation \(\sigma_1 \uplus \sigma_2 \uplus \nu_2\) to get \nmm{\nu_1: \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
-	The left side of the implication is proved with the left side of \hyp{9'} and \hyp{8'}, so we get
-	\[ \sigma_1 \uplus \nu_1 \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{7'} \]
-	Finally we can prove \goal{1'} with valuation \(\nu_1\) for the implicit \(\exists\) by admitting the left side of the implication and using \hyp{7'} for the right side.
-\end{proof}
-\begin{prop}[Limited composition correctness]\label{prop:cc'}
-Hole-subset simulation is correct w.r.t.\@ composition with automata without holes.
-\end{prop}
-Let \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\) be open automata, where \(J_2 = \emptyset\).
-Let \(k \in J_1\) and \(A \defobject A_1\subst{A_2}{k}\), with \(\OAg \defobject A\).
-Let \(v_1 \mapsto v_{1'}\) be the renaming for \(v_1 \in V_1\) in \(A\).
-Let \(\reach{A}\) be a witness that the composition \(A_1\subst{A_2}{k}\) is non-locking.
-The idea for the relation on configurations is that the copy of \(A_1\) in \(A\) do the same things as \(A_1\), as if we were trying to prove reflexivity.
-\[ R \defobject \mpar{\mpar{s_{1'}, s_2}, s_1} \mapsto \choice{\reach{A}\mpar{s_{1'}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1 & \text{if } s_{1'} = s_1 \\ \bot & \text{otherwise}} \]
-We want to prove that \(R\) is a hole-subset simulation of \(A\) by \(A_1\).
-\begin{proof}
-\item[1)] \(J = J_2 \uplus J_1 \setminus \mbrc{k} = \emptyset \uplus J_1 \setminus \mbrc{k} \subseteq J_1\)
-\item[2)] We use the fact that \(R\) doesn't constrain the behaviour of \(J_2\) and initial configuration is reachable:
-	\begin{align*}
-		\sigma_0 \uplus \sigma_{01} \vdash R\mpar{s_0, s_{01}} \iff & \mpar{\reach{A}\mpar{s_0} \wedge \bigwedge_{v_1 \in V_1} v_{1'} = v_1}\psubst{\sigma_{01'} \uplus \sigma_{02} \uplus \sigma_{01}} \\
-		\iff & \reach{A}\mpar{s_0}\psubst{\sigma_0} \wedge \bigwedge_\subbox{v_1 \in V_1} \sigma_{01'}\mpar{v_{1'}} = \sigma_{01}\mpar{v_1} \\
-		\iff & \sigma_0 \vdash \reach{A}\mpar{s_0}
-	\end{align*}
-\item[3)] Let \(s \defobject \mpar{s_{1'}, s_2} \in S\) and \(s_1 \in S_1\).
-	We want to prove both
-	\begin{align*}
-		& \bigsymb{\forall} t \defobject \OTg \in \fOT{s}, \bigsymb{\exists} \mpar{t_{1x} \defobject \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X}, \\
-		& \quad \mpar{\forall x \in X, J'_{1x} \cap J = J' \cap J_1} \\[-10pt]
-		& \nwedge V \uplus V_1 \uplus \fvars{t} \vdash R\mpar{s, s_1} \wedge g \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha = \alpha_{1x} \wedge \bigwedge_\subbox{j \in J'_{1x} \cap J} \beta_j = \beta_{1xj} \\[12pt]
-			\nwedge g_{1x} \wedge R\mpar{s', s'_{1x}}\psubst{\psi \uplus \psi_{1x}}
-		\end{array}} \goal{0}
-	\end{align*}
-	\[ V \uplus V_1 \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash R\mpar{s, s_1} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \goal{1} \]
-	Let \nmm{t \defobject \OTg \in \fOT{s}}, we know that \(t\) is obtained by composition so there is a generating transition \(t_1 \in \fOT{s_1}\) for which we will prove \goal{0}.
-	If \(s_{1'} \neq s_1\) we instead prove \goal{0} with the empty family.
-	\begin{gather}
-		\forall x \in X, J'_1 \cap J = J' \cap J_1 \goal{0'} \\
-		V \uplus V_1 \uplus \fvars{t} \vdash R\mpar{s, s_1} \wedge g \implies \alpha = \alpha_1 \wedge \bigwedge_\subbox{j \in J'_1 \cap J} \beta_j = \beta_{1j} \wedge g_1 \wedge R\mpar{s', s'_1}\psubst{\psi \uplus \psi_1} \goal{2}
-	\end{gather}
-\item[\goal{0'}:] \(t\) is a transition built from \(t_1\) so it has its holes.
-	Additionally either \(k \notin J'_1\) so \(J' = J'_1\) or \(k \in J'_1\) so \(J' = \emptyset \uplus J'_1 \setminus \mbrc{k}\) because \(A_2\) has no holes.
-	Either case \(J'_1 \cap J = J'_1 \setminus \mbrc{k} = \mpar{J'_1 \setminus \mbrc{k}} \cap J_1 = J' \cap J_1\).
-\item[\goal{2}:] Let \(\sigma: V \uplus V_1 \uplus \fvars{t} \to \values\).
-	We rename some variables in the definition domain of \(\sigma\) to get \(\nu: \fvars{t_1} \to \values\).
-	We use \(\nu\) to prove \goal{2}, get the left side of the implication as an hypothesis and break the right side of the implication:
-	\begin{gather}
-		\sigma \vdash R\mpar{s, s_1} \wedge g \hyp{1} \\
-		\sigma \uplus \nu \vdash \alpha = \alpha_1 \goal{2a} \\
-		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_1 \cap J} \beta_j = \beta_{1j} \goal{2b} \\
-		\sigma \uplus \nu \vdash g_1 \goal{2c} \\
-		\sigma \uplus \nu \vdash R\mpar{s', s'_1}\psubst{\psi \uplus \psi_1} \goal{2d}
-	\end{gather}
-	If \(s_{1'} \neq s_1\) then \hyp{1} is \(\sigma \vdash \bot\) so the proof is finished and the empty family worked.
-	Otherwise we can assume \(s_{1'} = s_1\) and break \hyp{1} into
-	\begin{gather}
-		\sigma \vdash \reach{A}\mpar{s} \hyp{1a} \\
-		\sigma \vdash \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1 \hyp{1b} \\
-		\sigma \vdash g \hyp{1c}
-	\end{gather}
-	\goal{2a} holds because composition doesn't change the produced action and the valuation coincide on the renamed variables.
-	\goal{2b} also holds because \(J'_1 \cap J = J'_1 \setminus \mbrc{k} = J'\), composition doesn't change the actions of the holes involved and the valuation coincide on the renamed variables.
-	\goal{2c} is proved using \hyp{1c} (\(g \iff g_1\) or \(g \iff g_1 \wedge \dots\)).
-	For \goal{2d} we first perform a transformation.
-	\begin{align*}
-		& \sigma \uplus \nu \vdash R\mpar{s', s'_1}\psubst{\psi \uplus \psi_1} \\
-		\iff & \sigma \uplus \nu \vdash \mpar{\reach{A}\mpar{s'} \wedge \bigwedge_{v_1 \in V_1} v_{1'} = v_1}\psubst{\psi_{1'} \uplus \psi_2 \uplus \psi_1} \\
-		\iff & \sigma \uplus \nu \vdash \reach{A}\mpar{s'}\psubst{\psi} \wedge \bigwedge_\subbox{v_1 \in V_1} \psi_{1'}\mpar{v_{1'}} = \psi_1\mpar{v_1} \\
-		\iff & \mpar{\sigma \vdash \reach{A}\mpar{s'}\psubst{\psi}} \wedge \mpar{\sigma \uplus \nu \vdash \bigwedge_\subbox{v_1 \in V_1} \psi_{1'}\mpar{v_{1'}} = \psi_1\mpar{v_1}}
-	\end{align*}
-	For the left side we use the preservation of reachability across transitions:
-	\[ \forall t \defobject \OTg \in T, \fvars{t} \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi} \hyp{2} \]
-	\hyp{2} is used for transition \(t\) with valuation \(\sigma\), the left side of the implication is \hyp{1a} and \hyp{1c}.
-	For the right side, the variables of \(\psi\) are in \(V_1 \uplus \fvars{t_1}\) so proving the following is sufficient:
-	\[ \sigma \uplus \nu \vdash \bigwedge_\subbox{v_1 \in V_1 \uplus \fvars{t_1}} v_{1'} = v_1 \goal{2d'} \]
-	By renaming of the definition domain, \(\nu\) coincides with \(\sigma\) on \(\fvars{t_1}\).
-	For the other variables we use \hyp{1b}.
-\item[\goal{1}:] Let \nmm{\sigma: V \uplus V_1 \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
-	We use dummy values for the variables in \nmm{\biguplus_\subbox{t \in \fOT{s}} \fvars{t}} to get the left side of the implication (independent from these values), immediately broken into
-	\begin{gather}
-		\sigma \vdash \reach{A}\mpar{s} \hyp{3a} \\
-		\sigma \vdash \bigwedge_\subbox{v_1 \in V_1} v_{1'} = v_1 \hyp{3b} \\
-		\sigma \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{3c}
-	\end{gather}
-	\(\reach{A}\) is a witness of the non-locking composition so we have the hypothesis:
-	\[ V \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{4} \]
-	We use \hyp{4} with valuation \(\sigma\) to get \nmm{\nu: \biguplus_\subbox{t \in \fOT{s}} \fvars{t} \to \values}.
-	The left side of the implication is proved with \hyp{3a} and \hyp{3c}, the right side gives the hypothesis:
-	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{4'} \]
-	We prove \goal{1} with valuation \(\nu\) by admitting the left side of the implication and using \hyp{4'}.
-\end{proof}
-\begin{prop}[Special composition correctness]
-If there is a hole-superset simulation of \(A_1\) by \(A_2\) and \(A_1\subst{A_3}{k}\) is non-locking, then there is a hole-superset simulation of \(A_1\subst{A_3}{k}\) by \(A_2\).
-Where \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\), \(A_3\) are open automata and \(k \in J_1 \setminus J_2\).
-\end{prop}
-Let \(\OAg[3] \defobject A_3\) and \(A \defobject A_1\subst{A_3}{k}\), with \(\OAg \defobject A\).
-Let \(R_{12}\) be a hole-superset simulation of \(A_1\) by \(A_2\) and \(\reach{A_1\subst{A_3}{k}}\) be a witness that \(A_1\subst{A_3}{k}\) is non-locking.
-The idea for the relation on configurations is to combine the non-locking composition and the already existing relation on configurations.
-\[ R \defobject \mpar{\mpar{s_1, s_3}, s_2} \mapsto R_{12}\mpar{s_1, s_2} \wedge \reach{A}\mpar{s_1, s_3} \]
-We want to prove that \(R\) is a hole-superset simulation of \(A\) by \(A_2\).
-\begin{proof}
-\item[1)] \(J = J_3 \uplus J_1 \setminus \mbrc{k} \supseteq J_3 \uplus J_2 \setminus \mbrc{k} \supseteq J_2 \setminus \mbrc{k} = J_2\)
-\item[2)] We use the fact that \(R_{12}\) relates initial configurations and that initial configuration is reachable:
-	\begin{align*}
-		\sigma_0 \uplus \sigma_{02} \vdash R\mpar{s_0, s_{02}} \iff & \sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03} \vdash R_{12}\mpar{s_{01}, s_{02}} \wedge \reach{A}\mpar{s_0} \\
-		\iff & \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar{\sigma_0 \vdash \reach{A}\mpar{s_0}}
-	\end{align*}
-\item[3)] Let \(s \defobject \mpar{s_1, s_3} \in S\) and \(s_2 \in S_2\).
-	We want to prove both
-	\begin{align*}
-		& \bigsymb{\forall} t \defobject \OTg \in \fOT{s}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
-		& \quad \mpar{\forall x \in X, J'_{2x} \cap J = J' \cap J_2} \\[-10pt]
-		& \nwedge V \uplus V_2 \uplus \fvars{t} \vdash R\mpar{s, s_2} \wedge g \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J} \beta_j = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R\mpar{s', s'_{2x}}\psubst{\psi \uplus \psi_{2x}}
-		\end{array}} \goal{0}
-	\end{align*}
-	\[ V \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \goal{1} \]
-	Let \nmm{t \defobject \OTg \in \fOT{s}}, we use the fact that \(R_{12}\) is a simulation from the states \(\mpar{s_1, s_2}\) to get the hypothesis:
-	\begin{align*}
-		& \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
-		& \quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
-		& \nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R_{12}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}} \hyp{1}
-	\end{align*}
-	Transition \(t\) is obtained by composition of \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}} and \nmm{t_3 \defobject \OTx{3}{}{3}{3} \in \fOT{s_3}} if \(k \in J'_1\) or by a the first transition and the state \(s_3\) if \(k \notin J'_1\).
-	We use \hyp{1} with the transition \(t_1\) to get
-	\begin{gather*}
-		\mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X} \\
-		\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2 \hyp{1'} \\
-		V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R_{12}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}} \hyp{1"}
-	\end{gather*}
-	We will prove \goal{0} for the family \(t_{2x}\), the new goals are
-	\begin{gather}
-		\forall x \in X, J'_{2x} \cap J = J' \cap J_2 \goal{0'} \\
-		V \uplus V_2 \uplus \fvars{t} \vdash R\mpar{s, s_2} \wedge g \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J} \beta_j = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R\mpar{s', s'_{2x}}\psubst{\psi \uplus \psi_{2x}}
-		\end{array}} \goal{2}
-	\end{gather}
-\item[\goal{0'}:] Let \(x \in X\)
-	\begin{align*}
-		J'_{2x} \cap J & = J'_{2x} \cap \mpar{J_3 \uplus J_1 \setminus \mbrc{k}} \\
-		& = J'_{2x} \cap J_1 & \text{by } k \in J_1 \setminus J_2 \text{ and } \emptyset = J_3 \cap J_1 \supseteq J_3 \cap J_2 \hyp{2} \\
-		& = J'_1 \cap J_2 & \text{by \hyp{1'}} \\
-		& = \mpar{J'_1 \uplus J'_3} \cap J_2 \\
-		& = J' \cap J_2
-	\end{align*}
-\item[\goal{2}:] Let \nmm{\sigma: V \uplus V_2 \uplus \fvars{t} \to \values}.
-	We use dummy values for the variables in \nmm{\biguplus_\subbox{t_{2x} \in \fOT{s_2}} \fvars{t_{2x}}} to get the left side of the implication (independent from these values), immediately broken into
-	\begin{gather}
-		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{3a} \\
-		\sigma \vdash \reach{A}\mpar{s} \hyp{3b} \\
-		\sigma \vdash g \hyp{3c}
-	\end{gather}
-	We use \hyp{1"} with valuation \(\sigma\) on variables \(V_1 \uplus V_2 \uplus \fvars{t_1}\), which is possible because the composition of transitions doesn't remove any variable.
-	Then we get the values of the implicit \(\exists\) in \nmm{\nu: \biguplus_{x \in X} \fvars{t_{2x}}}.
-	The left side of the implication is proved with \hyp{3a} and \hyp{3c}.
-	So we get a \(x \in X\) such that
-	\begin{gather}
-		\sigma \uplus \nu \vdash \alpha_1 = \alpha_{2x} \hyp{4a} \\
-		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \hyp{4b} \\
-		\sigma \uplus \nu \vdash g_{2x} \hyp{4c} \\
-		\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \hyp{4d}
-	\end{gather}
-	In order to progress on \goal{2} we give valuation \(\nu\) for the implicit \(\exists\), admit the left side of the implication and choose to prove the branch \(x\):
-	\begin{gather}
-		\sigma \uplus \nu \vdash \alpha = \alpha_{2x} \goal{2a} \\
-		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_{2x} \cap J} \beta_j = \beta_{2xj} \goal{2b} \\
-		\sigma \uplus \nu \vdash g_{2x} \goal{2c} \\
-		\sigma \uplus \nu \vdash R\mpar{s', s'_{2x}}\psubst{\psi \uplus \psi_{2x}} \goal{2d}
-	\end{gather}
-	\goal{2a} is proved by \hyp{4a} (\(\alpha = \alpha_1\)).
-	\goal{2b} is proved using \hyp{4b} because \(J'_{2x} \cap J = J'_{2x} \cap J_1 = J'_1 \cap J_2\) (\hyp{2} and \hyp{1'}) and \(\forall j \in J'_1, \beta_{1j} = \beta_j\) (transition comes from composition).
-	\goal{2c} is proved by \hyp{4c}.
-	For \goal{2d} we first perform a transformation.
-	\begin{align*}
-		& \sigma \uplus \nu \vdash R\mpar{s', s'_{2x}}\psubst{\psi \uplus \psi_{2x}} \\
-		\iff & \sigma \uplus \nu \vdash \mpar{R_{12}\mpar{s'_1, s'_{2x}} \wedge \reach{A}\mpar{s'}}\psubst{\psi_1 \uplus \psi_{2x} \uplus \psi_3} \\
-		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \reach{A}\mpar{s'}\psubst{\psi}}
-	\end{align*}
-	The left side is \hyp{4d}.
-	For the right side we use the preservation of reachability across transitions:
-	\[ \forall t \defobject \OTg \in T, \fvars{t} \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi} \hyp{5} \]
-	\hyp{5} is used for transition \(t\) with valuation \(\sigma\), the left side of the implication is \hyp{3b} and \hyp{3c}.
-\item[\goal{1}:]
-	Let \nmm{\sigma: V \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \to \values}.
-	We use dummy values for the variables in \nmm{\biguplus_\subbox{t \in \fOT{s}} \fvars{t}} to get the left side of the implication (independent from these values), immediately broken into
-	\begin{gather}
-		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{6a} \\
-		\sigma \vdash \reach{A}\mpar{s} \hyp{6b} \\
-		\sigma \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{6c}
-	\end{gather}
-	\(R_{12}\) is a simulation and \(\reach{A}\) is a witness of the non-locking composition so we have the hypotheses:
-	\begin{gather}
-		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{7} \\
-		V \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{8}
-	\end{gather}
-	We use \hyp{7} with valuation \(\sigma\) to get \nmm{\nu: \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
-	The left side of the implication is proved with \hyp{6a} and \hyp{6c}, the right side gives the hypothesis:
-	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{7'} \]
-	We then use \hyp{8} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t \in \fOT{s}} \fvars{t}}.
-	The left side of the implication is proved using \hyp{6b} and \hyp{7'}, the right side gives:
-	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \hyp{8'} \]
-	We prove \goal{1} with valuation \(\nu'\) by admitting the left side of the implication and using \hyp{8'}.
-\end{proof}
-The hole-subset simulation can only tell if there is a refinement when the composed automata have no holes.
-To lift this limitation we need to allow adding holes which doesn't have a direct interpretation.
-
-At first a solution using a function mapping the action performed by the new holes in the composition to the ones performed by removed hole in the base automaton was explored.
-It was abandoned because the base automaton has nothing intelligent to tell about the action required by the composed automata.
-That is the reason the hole-superset simulation doesn't constrain the action performed by the added holes.
-The solution adopted is to give a meaning to adding hole and only adding in a simulation.
-With the hole-superset simulation we have an interpretation to added holes:
-They are holes imposing a restriction on the transition variables.
-However with that solution we cannot remove holes so we cannot express composition correctness, hence the need of the special composition correctness for hole-superset simulation.
-
-For composition correctness, using only one of the hole-\(\triangle\) simulations cannot tell that a non-locking composition with any open automaton is a refinement of the base automaton because we need at the same time to add and remove holes.
-If we build the refinement relation as the transitive closure of all the hole-\(\triangle\) simulations then an issue arise.
-The transitivity propriety causes that when a hole present in both extrema of the chain but absent in an intermediate automaton, there is a refinement between the extrema of the chain.
-In that case all the constraint on holes actions are lifted even if we would like to require an equality of these actions on the transitive closure.
-
-\section{Refinement relation for open automata}\label{sec:refinement}
-One solution to solve the issue presented at the end of previous section, that is to keep transitivity and constraints on holes actions from same holes, is to keep track of which holes are in common at each step of refinement.
-The transitive refinement will have to either rename the holes without constraints or explicitly say which holes have constraints.
-\begin{defi}[Open automata refinement]
-For two open automata \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a refinement of \(A_2\) looking at \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), is defined as:
-\begin{multline*}
-	\exists R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2], \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge \forall \mpar{s_1, s_2} \in S_1 \times S_2, \\
-	\mpar{\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\[12pt]
-		\quad \mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H} \\[-10pt]
-		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \\
-			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}} \\
-	\end{array}} \\
-	\wedge V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
-\end{multline*}
-Giving \(R\) and \(H\) is sufficient to characterise the refinement, so we call \(\mpar{R, H}\) a hole-tracking simulation of \(A_1\) by \(A_2\).
-Hole in \(H\) are called tracked holes.
-\end{defi}
-\(R\) is a kind of hole-\(\triangle\) simulation but without the \(\triangle\) constraint on hole sets.
-On top of that every action of the holes outside \(H\) is unconstrained in the related automata.
-
-This definition is close to the refinement relation deduced from hole-\(\triangle\) simulations.
-Actually the latter are particular cases of this one.
-Let \(A_1 \defobject \OAg[1]\) and \(A_2 \defobject \OAg[2]\) be two open automata.
-If \(J_1 = J_2\), we have \(\wrel{A_1}{A_2}{J_1}\) if and only if there is a hole-equal simulation of \(A_1\) by \(A_2\).
-If \(J_1 \subseteq J_2\), we have \(\wrel{A_1}{A_2}{J_1}\) if and only if there is a hole-subset simulation of \(A_1\) by \(A_2\).
-Finally if \(J_1 \supseteq J_2\), we have \(\wrel{A_1}{A_2}{J_2}\) if and only if there is a hole-superset simulation of \(A_1\) by \(A_2\).
-
-The idea behind the set of tracked holes is that a tracked hole is guaranteed to behave well with composition.
-To have guarantees on a hole when performing successive refinement we must keep the hole tracked in every refinement step.
-Otherwise everything happens as if the hole of the most refined automaton is not the same as the one with the same name in the least refined automaton.
-It shouldn't be surprising if at some refinement step all the constraints on a hole are lost, that in the whole process they also are.
-It is the best we can do and if someone want to keep the constraint, then they should choose wisely the intermediate automata used for the refinement.
-
-In terms of transitivity, for the open automata refinement, the strongest property we can prove becomes \(\wrel{A}{B}{X} \wedge \wrel{B}{C}{Y} \implies \wrel{A}{C}{X \cap Y}\).
-For a weaker property we can use the fact that \(\wrel{A_1}{A_2}{H} \implies \wrel{A_1}{A_2}{H'}\) when \(H' \subseteq H\).
-Transitivity behaves the same as if the holes outside the intersection were renamed to avoid conflicts in the first place.
-This in combination with the fact that hole-\(\triangle\) simulation are a particular case of hole-tracking simulation makes the combination of the transitivity proofs of hole-\(\triangle\) simulation sufficient to prove transitivity.
-
-Not renaming conflicting holes still have an interest.
-If we are trying to build an automaton \(A\) with several constraints \(\wrel{A}{A_i}{J_{Ai}}, i \in I\) (as done in B method \cite{cansell:inria-00099794}) and each \(A_i\) is a refinement of some automaton \(C\) then we can have each \(A_i\) constrain a different subset of \(A\)'s holes.
-On each individual path \(A \leq_{J_{Ai}} A_i \leq_{J_{Ai}} C\), some holes of \(A\) are unconstrained but when considering all path they are all constrained.
-However this doesn't implies \(A \leq_{\bigcup_{i \in I} J_{Ai}} C\), it has to be checked separately.
-\begin{exi}
-\begin{figure}
-\centering
-\input{identity.tex}
-\vrule
-\input{any.tex}
-\vrule
-\input{handshake_comp}
-\caption{On the left: Generic identity on holes; On the center: Any action automaton; On the right: Handshake composition.}
-\label{fig:sevpathref}
-\end{figure}
-We have two refinement paths when \(h\) is replaced by \(l\) and by \(r\) in identity on holes (left of Figure \ref{fig:sevpathref}): the parallel composition (left of Figure \ref{fig:hisim}) is a refinement of the identity on holes, which is a refinement of the handshake composition (right of Figure \ref{fig:sevpathref}).
-However we do not have the parallel composition being a refinement of the handshake composition looking at \(\mbrc{l, r}\).
-
-The example also shows a property worth mentioning.
-The holes not tracked are equivalent to having the any action automaton (center of Figure \ref{fig:sevpathref}) composed.
-Actually all the previous refinement are both ways: we can compose the any action automaton in hole \(r\) of the parallel composition to get the other way of the refinement with the identity on holes by composition correctness, and we transform the transition from the identity on holes into the one of the handshake composition by hole-superset refinement.
-\end{exi}
-The other interesting properties left to check are correctness w.r.t.\@ composition, context refinement, composition congruence and compatibility with FH-bisimulation.
-They have to be slightly modified because of the tracked holes set.
-Proving them for the open automata refinement will also prove them for each hole-\(\triangle\) simulation as they are just particular cases.
-\begin{thm}
-Open automata refinement is correct w.r.t.\@ composition.
-The tracked holes are the holes of the base automaton minus the composed hole.
-\end{thm}
-\begin{proof}
-We will decompose composition into two refinement steps, transitivity will complete the proof.
-Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(k \in J_1\) such that \(A_1\subst{A_2}{k}\) is non-locking.
-We pose \(A'_2\) as \(A_2\) stripped of its holes.
-\begin{align*}
-	A'_2 \defobject & \OA{S_2}{s_{02}}{V_2}{\sigma_{02}}{\emptyset}{T'_2} \\
-	T'_2 \defobject & \mset{\OT{s}{s'}{\alpha}{\mbrc{}}{g}{\psi}}{\OTg \in T_2}
-\end{align*}
-By limited composition correctness we have \(\wrel{A_1\subst{A'_2}{k}}{A_1}{J_1 \setminus \mbrc{k}}\).
-Adding holes and binding actions to the new holes is a refinement for hole-superset simulation so we have \(\wrel{A_1\subst{A_2}{k}}{A_1\subst{A'_2}{k}}{J_1 \setminus \mbrc{k}}\).
-By transitivity we have composition correctness.
-\end{proof}
-\begin{thm}[Context refinement]
-Open automata refinement is context refining when the composition happens in a tracked hole:
-Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\).
-Let \(\mpar{R_{12}, H_{12}}\) be a hole-tracking simulation of \(A_1\) by \(A_2\), \(k \in H_{12}\) and \(\reach{A_1\subst{A_3}{k}}\) be a witness that \(A_1\subst{A_3}{k}\) is non-locking.
-Let \(H \defobject J_3 \uplus H_{12} \setminus \mbrc{k}\).
-We have \(\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{H}\).
-\end{thm}
-Let \(A_{13} \defobject A_1\subst{A_3}{k}\) and \(A_{23} \defobject A_2\subst{A_3}{k}\).
-Let \(v_3 \mapsto v_{3x}\) is the renaming for \(v_3 \in V_3\) in \(A_{x3}\).
-We pose \(\OAg[13] \defobject A_{13}\) and \(\OAg[23] \defobject A_{23}\).
-We have \(\reach{A_{13}} = \reach{A_1\subst{A_3}{k}}\).
-The idea for the relation on configurations is that \(A_2\) simulates \(A_1\) while \(A_3\) does the same things in both compositions in the hole \(k\).
-\[ R \defobject \mpar{\mpar{s_1, s_{31}}, \mpar{s_2, s_{32}}} \mapsto \choice{R_{12}\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_1, s_{31}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} & \text{if } s_{31} = s_{32} \\ \bot & \text{otherwise}} \]
-We want to prove that \(\mpar{R, H}\) is a witness of \(\wrel{A_{13}}{A_{23}}{H}\).
-\begin{proof}
-\item[1)] \(H = J_3 \uplus H_{12} \setminus \mbrc{k} \subseteq J_3 \uplus \mpar{J_1 \cap J_2} \setminus \mbrc{k} = \mpar{J_3 \uplus J_1 \setminus \mbrc{k}} \cap \mpar{J_3 \uplus J_2 \setminus \mbrc{k}} = J_{13} \cap J_{23}\)
-\item[2)] We use the fact that \(R_{12}\) relates inital configurations, initial configuration is reachable, and \(\sigma_{031}\) and \(\sigma_{032}\) are renaming of \(\sigma_{03}\):
-	\begin{align*}
-		& \sigma_{013} \uplus \sigma_{023} \vdash R\mpar{s_{013}, s_{023}} \\
-		\iff & R\mpar{\mpar{s_{01}, s_{031}}, \mpar{s_{02}, s_{031}}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{031} \uplus \sigma_{032}} \\
-		\iff & R_{12}\mpar{s_{01}, s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}\psubst{\sigma_{013}} \wedge \mpar{\bigwedge_{v_3 \in V_3} v_{31} = v_{32}}\psubst{\sigma_{031} \uplus \sigma_{032}} \\
-		\iff & \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}} \wedge \bigwedge_\subbox{v_3 \in V_3} \sigma_{031}\mpar{v_{31}} = \sigma_{032}\mpar{v_{32}} \\
-		\iff & \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}} \wedge \top
-	\end{align*}
-\item[3)] Let \(s_{13} \defobject \mpar{s_1, s_{31}} \in S_{13}\) and \(s_{23} \defobject \mpar{s_2, s_{32}} \in S_{23}\).
-	We want to prove both
-	\begin{align*}
-		& \bigsymb{\forall} t_{13} \defobject \OTx{13}{}{13}{13} \in \fOT{s_{13}}, \bigsymb{\exists} \mpar{t_{23x} \defobject \OTx{23}{x}{23x}{23x} \in \fOT{s_{23}}}^{x \in X}, \\
-		& \quad \mpar{\forall x \in X, J'_{23x} \cap H = J'_{13} \cap H} \\[-10pt]
-		& \nwedge V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H} \beta_{13j} = \beta_{23xj} \\[12pt]
-			\nwedge g_{23x} \wedge R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
-		\end{array}} \goal{0}
-	\end{align*}
-	\[ V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash R\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \goal{1} \]
-	Let \nmm{t_{13} \defobject \OTx{13}{}{13}{13} \in \fOT{s_{13}}}, we use the fact that \(R_{12}\) is a simulation from the states \(\mpar{s_1, s_2}\) to get the hypothesis:
-	\begin{align*}
-		& \bigsymb{\forall} t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
-		& \quad \mpar{\forall x \in X, J'_{2x} \cap H_{12} = J'_1 \cap H_{12}} \\[-10pt]
-		& \nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R_{12}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H_{12}} \beta_{1j} = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}} \hyp{1}
-	\end{align*}
-	Transition \(t_{13}\) is obtained in \(A_{13}\) by composition of two transitions \nmm{t_1 \defobject \OTx{1}{}{1}{1} \in \fOT{s_1}} and \nmm{t_{31} \defobject \OTx{31}{}{31}{31} \in \fOT{s_{31}}} if \(k \in J'_1\) or by a the first transition and the state \(s_{31}\) if \(k \notin J'_1\).
-	We use \hyp{1} with the transition \(t_1\) to get
-	\begin{gather*}
-		\mpar{t_{2x} \defobject \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X} \\
-		\forall x \in X, J'_{2x} \cap H_{12} = J'_1 \cap H_{12} \hyp{1'} \\
-		V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R_{12}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H_{12}} \beta_{1j} = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}} \hyp{1"}
-	\end{gather*}
-	To build the family of transitions we need to know if \(k \in J'_{2x}\) for a every \(x \in X\).
-	We have \(k \in H_{12}\) so by \hyp{1'} \(k \in J'_{2x} \iff k \in J'_1\).
-	If \(s_{31} = s_{32}\) we can copy \(t_{31}\) into \nmm{t_{32} = \OTx{32}{}{32}{32}} to avoid conflicts.
-	We also name \(t_3\) the original transition from \(T_3\).
-	We build the family of transition generated by the family \(t_{2x}^{x \in X}\):
-	\[ t_{23x}^{x \in X} \defobject x \mapsto \choice{
-		\OT{\mpar{s_2, s_{32}}}{\mpar{s'_{2x}, s'_{32}}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x} \setminus \mbrc{k}} \uplus \beta_{3j}^{j \in J'_{32}}}{g_{2x} \wedge g_{32} \wedge \alpha_{32} = \beta_{2xk}}{\psi_{2x} \uplus \psi_{32}} & \text{if } k \in J'_{2x} \\
-		\OT{\mpar{s_2, s_{32}}}{\mpar{s'_{2x}, s_{32}}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_2}}{g_2}{\psi_2} & \text{otherwise}
-	} \]
-	Otherwise \(s_{31} \neq s_{32}\) and we can give the empty family, it won't cause any issue.
-	We will prove \goal{0} for the family \(t_{23x}^{x \in X}\), the new goals are
-	\begin{gather}
-		\forall x \in X, J'_{23x} \cap H = J'_{13} \cap H \goal{0'} \\
-		V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{13} \cap H} \beta_{13j} = \beta_{23xj} \\[12pt]
-			\nwedge g_{23x} \wedge R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
-		\end{array}} \goal{2}
-	\end{gather}
-\item[\goal{0'}:] Let \(x \in X\), by case on \(k \in J'_1\).
-	\begin{align*}
-		\text{If } k \in J'_1: && J'_{23x} \cap H & = \mpar{J'_{32} \uplus J'_{2x} \setminus \mbrc{k}} \cap \mpar{J_3 \uplus H_{12} \setminus \mbrc{k}} \\
-		&&& = \mpar{J'_{31} \cap J_3} \uplus \mpar{J'_{2x} \cap H_{12}} \setminus \mbrc{k} & \text{by } J'_{32} = J'_{31} \\
-		&&& = \mpar{J'_{31} \cap J_3} \uplus \mpar{J'_1 \cap H_{12}} \setminus \mbrc{k} & \text{by \hyp{1'}} \\
-		&&& = \mpar{J'_{31} \uplus J'_1 \setminus \mbrc{k}} \cap \mpar{J_3 \uplus H_{12} \setminus \mbrc{k}} \\
-		&&& = J'_{13} \cap H \\
-		\text{If } k \notin J'_1: && J'_{23x} \cap H & = \mpar{J'_{2x} \setminus \mbrc{k}} \cap \mpar{J_3 \uplus H_{12} \setminus \mbrc{k}} \\
-		&&& = \mpar{J'_{2x} \cap H_{12}} \setminus \mbrc{k} \\
-		&&& = \mpar{J'_1 \cap H_{12}} \setminus \mbrc{k} & \text{by \hyp{1'}} \\
-		&&& = \mpar{J'_1 \setminus \mbrc{k}} \cap \mpar{J_3 \uplus H_{12} \setminus \mbrc{k}} \\
-		&&& = J'_{13} \cap H
-	\end{align*}
-\item[\goal{2}:] Let \(\sigma: V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \to \values\).
-	We use dummy values for the variables in \nmm{\biguplus_{x \in X} \fvars{t_{23x}}} to get the left side of the implication as an hypothesis (independent from these values):
-	\[ \sigma \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \hyp{2} \]
-	If \(s_{31} \neq s_{32}\) then this hypothesis is \(\sigma \vdash \bot\), the empty family works and the proof is finished.
-	We can assume \(s_{31} = s_{32}\) and break \hyp{2} into
-	\begin{gather}
-		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{2a} \\
-		\sigma \vdash \reach{A_{13}}\mpar{s_{13}} \hyp{2b} \\
-		\sigma \vdash \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32} \hyp{2c} \\
-		\sigma \vdash g_{13} \hyp{2d}
-	\end{gather}
-	We use \hyp{1"} with valuation \(\sigma\) on variables \(V_1 \uplus V_2 \uplus \fvars{t_1}\), which is possible because the composition of transitions doesn't remove any variable (the simplification steps do, they give bisimilar automata).
-	Then we get the values of the implicit \(\exists\) in \nmm{\nu: \biguplus_{x \in X} \fvars{t_{2x}}}.
-	The left side of the implication is proved with \hyp{2a} and \hyp{2d}.
-	So we get a \(x \in X\) such that
-	\begin{gather}
-		\sigma \uplus \nu \vdash \alpha_1 = \alpha_{2x} \hyp{3a} \\
-		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \hyp{3b} \\
-		\sigma \uplus \nu \vdash g_{2x} \hyp{3c} \\
-		\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \hyp{3d}
-	\end{gather}
-	If \(k \in J'_1\), we extend the valuation \(\nu\) to cover the variables of \(t_3\) in \(t_{23x}\) using their value in \(t_{13}\), \(\nu' \defobject \nu \uplus \mset{v_{32} \mapsto \sigma\mpar{v_{31}}}{v_3 \in \fvars{t_3}}\).
-	Otherwise \(\nu' \defobject \nu\).
-	We progress on \goal{2} by giving the valuation \(\sigma \uplus \nu'\) to the implicit \(\exists\), admitting the left side of the implication and choosing to prove the branch \(x\) of the disjunction:
-	\begin{gather}
-		\sigma \uplus \nu' \vdash \alpha_{13} = \alpha_{23x} \goal{3a} \\
-		\sigma \uplus \nu' \vdash \bigwedge_\subbox{j \in J'_{23x} \cap H} \beta_{13j} = \beta_{23xj} \goal{3b} \\
-		\sigma \uplus \nu' \vdash g_{23x} \goal{3c} \\
-		\sigma \uplus \nu' \vdash R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}} \goal{3d}
-	\end{gather}
-	Because composition doesn't change the produced actions nor its variables, \goal{3a} is proved by \hyp{3a}.
-	\goal{3b} holds because the valuations for the actions of the holes in \(J_3\) coincide by definition of \(\nu'\) and by \hyp{3b} for the others.
-	For \goal{3c} we have two cases, if \(k \notin J'_1\) then \(g_{23x} \iff g_{2x}\) and \hyp{3c} is sufficient, if \(k \in J'_1\) then \(g_{23x} \iff g_{2x} \wedge g_3 \wedge \alpha_3 = \beta_{2xk}\) so we also need \hyp{2d} (\(g_{13} \iff g_1 \wedge g_3 \wedge \alpha_3 = \beta_{1k}\)) and \hyp{3b} for the value \(k\) (\(\beta_{1k} = \beta_{2xk}\)).
-	For \goal{3d} we first perform a transformation.
-	\begin{align*}
-		& \sigma \uplus \nu' \vdash R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}} \\
-		\iff & \sigma \uplus \nu' \vdash \mpar{R_{12}\mpar{s'_1, s'_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}} \wedge \bigwedge_\subbox{v_3 \in V_3} v_{31} = v_{32}}\psubst{\psi_1 \uplus \psi_{31} \uplus \psi_{2x} \uplus \psi_{32}} \\
-		\iff & \sigma \uplus \nu' \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}} \wedge \bigwedge_\subbox{v_3 \in V_3} \psi_{31}\mpar{v_{31}} = \psi_{32}\mpar{v_{32}} \\
-		\iff & \mpar{\sigma \uplus \nu \vdash R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}} \wedge \mpar{\sigma \vdash \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}}} \wedge \mpar{\sigma \uplus \nu' \vdash \bigwedge_\subbox{v_3 \in V_3} \psi_{31}\mpar{v_{31}} = \psi_{32}\mpar{v_{32}}}
-	\end{align*}
-	The left side is \hyp{3d}.
-	For the middle part we use the preservation of reachability across transitions:
-	\[ \forall t_{13} \defobject \OTx{13}{}{13}{13} \in T_{13}, \fvars{t_{13}} \vdash \reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s'_{13}}\psubst{\psi_{13}} \hyp{4} \]
-	\hyp{4} is used for transition \(t_{13}\) with valuation \(\sigma\), the left side of the implication is \hyp{2b} and \hyp{2d}.
-
-	For the right side, the variables of \(\psi_{13}\) and \(\psi_{23}\) are renaming of \(\psi_3\) on variables in \(\fvars{t_3}\) or do not involve these variables at all, so either \hyp{2c} is sufficient, or additionnaly proving the following is sufficient:
-	\[ \nu' \vdash \bigwedge_\subbox{v_3 \in \fvars{t_3}} v_{31} = v_{32} \]
-	Which holds by definition of \(\nu'\).
-\item[\goal{1}:] Let \nmm{\sigma: V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \to \values}.
-	We use dummy values for the variables in \nmm{\biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}}} to get the left side of the implication (independent from these values), immediately broken into
-	\begin{gather}
-		\sigma \vdash R_{12}\mpar{s_1, s_2} \hyp{5a} \\
-		\sigma \vdash \reach{A_{13}}\mpar{s_{13}} \hyp{5b} \\
-		\sigma \vdash \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \hyp{5c}
-	\end{gather}
-	\(R_{12}\) is a simulation and \(\reach{A_{13}}\) is a witness of the non-locking composition so we have the hypotheses:
-	\begin{gather}
-		V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6} \\
-		V_{13} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{7}
-	\end{gather}
-	We use \hyp{6} with valuation \(\sigma\) projected on the variables from generating transitions in \(A_2\) to get \nmm{\nu: \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \to \values}.
-	The left side of the implication is proved using \hyp{5a} and \hyp{5c} because the guards from transitions of \(A_2\) are still in transitions of \(A_{23}\), the right side gives:
-	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \hyp{6'} \]
-	We then use \hyp{7} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}}}.
-	The left side of the implication is proved using \hyp{5b} and \hyp{6'}, the right side gives:
-	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \hyp{7'} \]
-	\goal{1} is proved for valuation \(\nu'\) by admitting the left side and using \hyp{7'}.
-\end{proof}
-\begin{thm}[Composition congruence]
-Open automata refinement is congruent for composition:
-Let \(A_1 \defobject \OAg[1]\), \(A_2 \defobject \OAg[2]\) and \(A_3 \defobject \OAg[3]\).
-Let \(k \in J_1\), \(\mpar{R_{23}, H_{23}}\) be a hole-tracking simulation of \(A_2\) by \(A_3\) and \(\reach{A_1\subst{A_2}{k}}\) be a witness that \(A_1\subst{A_2}{k}\) is non-locking.
-Let \(H \defobject H_{23} \uplus J_1 \setminus \mbrc{k}\).
-We have \(\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{H}\).
-\end{thm}
-We pose \(\OAg[21] \defobject A_{21}\) and \(\OAg[31] \defobject A_{31}\).
-Let \(v_1 \mapsto v_{1x}\) is the renaming for \(v_1 \in V_1\) in \(A_{x1}\).
-The idea for the relation on configurations is that \(A_3\) simulates \(A_2\) while \(A_1\) does the same things in both compositions.
-\[ R \defobject \mpar{\mpar{s_{12}, s_2}, \mpar{s_{13}, s_3}} \mapsto \choice{R_{23}\mpar{s_2, s_3} \wedge \reach{A_{21}}\mpar{s_{12}, s_2} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{12} = v_{13} & \text{if } s_{12} = s_{13} \\ \bot & \text{otherwise}} \]
-We want to prove that \(\mpar{R, H}\) is a witness of \(\wrel{A_{21}}{A_{31}}{H}\).
-\begin{proof}
-\item[1)] \(H = H_{23} \uplus J_1 \setminus \mbrc{k} \subseteq \mpar{J_2 \cap J_3} \uplus J_1 \setminus \mbrc{k} = \mpar{J_2 \uplus J_1 \setminus \mbrc{k}} \cap \mpar{J_3 \uplus J_1 \setminus \mbrc{k}} = J_{21} \cap J_{31}\)
-\item[2)] We use the fact that \(R_{23}\) relates inital configurations, initial configuration is reachable, and \(\sigma_{012}\) and \(\sigma_{013}\) are renaming of \(\sigma_{01}\):
-	\begin{align*}
-		& \sigma_{021} \uplus \sigma_{031} \vdash R\mpar{s_{021}, s_{031}} \\
-		\iff & R\mpar{\mpar{s_{012}, s_{02}}, \mpar{s_{013}, s_{03}}}\psubst{\sigma_{012} \uplus \sigma_{02} \uplus \sigma_{013} \uplus \sigma_{03}} \\
-		\iff & R_{23}\mpar{s_{02}, s_{03}}\psubst{\sigma_{02} \uplus \sigma_{03}} \wedge \reach{A_{21}}\mpar{s_{021}}\psubst{\sigma_{021}} \wedge \mpar{\bigwedge_{v_1 \in V_1} v_{12} = v_{13}}\psubst{\sigma_{012} \uplus \sigma_{013}} \\
-		\iff & \mpar{\sigma_{02} \uplus \sigma_{03} \vdash R_{23}\mpar{s_{02}, s_{03}}} \wedge \mpar{\sigma_{021} \vdash \reach{A_{21}}\mpar{s_{021}}} \wedge \bigwedge_\subbox{v_1 \in V_1} \sigma_{012}\mpar{v_{12}} = \sigma_{013}\mpar{v_{13}} \\
-		\iff & \mpar{\sigma_{02} \uplus \sigma_{03} \vdash R_{23}\mpar{s_{02}, s_{03}}} \wedge \mpar{\sigma_{021} \vdash \reach{A_{21}}\mpar{s_{021}}} \wedge \top
-	\end{align*}
-\item[3)] Let \(s_{21} \defobject \mpar{s_{12}, s_2} \in S_{21}\) and \(s_{31} \defobject \mpar{s_{13}, s_3} \in S_{31}\).
-	We want to prove both
-	\begin{align*}
-		& \bigsymb{\forall} t_{21} \defobject \OTx{21}{}{21}{21} \in \fOT{s_{21}}, \bigsymb{\exists} \mpar{t_{31x} \defobject \OTx{31}{x}{31x}{31x} \in \fOT{s_{31}}}^{x \in X}, \\
-		& \quad \mpar{\forall x \in X, J'_{31x} \cap H = J'_{21} \cap H} \\[-10pt]
-		& \nwedge V_{21} \uplus V_{31} \uplus \fvars{t_{21}} \vdash R\mpar{s_{21}, s_{31}} \wedge g_{21} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{21} = \alpha_{31x} \wedge \bigwedge_\subbox{j \in J'_{31x} \cap H} \beta_{21j} = \beta_{31xj} \\[12pt]
-			\nwedge g_{31x} \wedge R\mpar{s'_{21}, s'_{31x}}\psubst{\psi_{21} \uplus \psi_{31x}}
-		\end{array}} \goal{0}
-	\end{align*}
-	\[ V_{21} \uplus V_{31} \uplus \biguplus_\subbox{t_{31} \in \fOT{s_{31}}} \fvars{t_{31}} \vdash R\mpar{s_{21}, s_{31}} \wedge \bigvee_\subbox{t_{31} \in \fOT{s_{31}}} \fguard{t_{31}} \implies \bigvee_\subbox{t_{21} \in \fOT{s_{21}}} \fguard{t_{21}} \goal{1} \]
-	Let \nmm{t_{21} \defobject \OTx{21}{}{21}{21} \in \fOT{s_{21}}}, it is obtained by composition of \nmm{t_{12} \defobject \OTx{12}{}{12}{12} \in \fOT{s_{12}}} and \nmm{t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}} if \(k \in J'_{12}\) or by a the first transition and the state \(s_2\) if \(k \notin J'_{12}\).
-	If \(k \in J'_{12}\), we use the fact that \(R_{23}\) is a simulation from the states \(\mpar{s_2, s_3}\) to get the hypothesis:
-	\begin{align*}
-		& \bigsymb{\forall} t_2 \defobject \OTx{2}{}{2}{2} \in \fOT{s_2}, \bigsymb{\exists} \mpar{t_{3x} \defobject \OTx{3}{x}{3x}{3x} \in \fOT{s_3}}^{x \in X}, \\
-		& \quad \mpar{\forall x \in X, J'_{3x} \cap H_{23} = J'_2 \cap H_{23}} \\[-10pt]
-		& \nwedge V_2 \uplus V_3 \uplus \fvars{t_2} \vdash R_{23}\mpar{s_2, s_3} \wedge g_2 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_2 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x} \cap H_{23}} \beta_{2j} = \beta_{3xj} \\[12pt]
-			\nwedge g_{3x} \wedge R_{23}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
-		\end{array}} \hyp{1}
-	\end{align*}
-	hypothesis that we use with the transition \(t_2\) to get
-	\begin{gather*}
-		\mpar{t_{3x} \defobject \OTx{3}{x}{3x}{3x} \in \fOT{s_3}}^{x \in X} \\
-		\forall x \in X, J'_{3x} \cap H_{23} = J'_2 \cap H_{23} \hyp{1'} \\
-		V_2 \uplus V_3 \uplus \fvars{t_2} \vdash R_{23}\mpar{s_2, s_3} \wedge g_2 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_2 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x} \cap H_{23}} \beta_{2j} = \beta_{3xj} \\[12pt]
-			\nwedge g_{3x} \wedge R_{23}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
-		\end{array}} \hyp{1"}
-	\end{gather*}
-	In the case \(s_{12} \neq s_{13}\) we can give the empty family, it won't cause any issue.
-	Otherwise \(s_{12} = s_{13}\) so we can copy \(t_{12}\) into \nmm{t_{13} = \OTx{13}{}{13}{13}} to avoid conflicts.
-	We also name \(t_1\) the original transition from \(T_1\).
-	We build the family of transition generated by \(t_{13}\):
-	\[ t_{31x}^{x \in X} \defobject \choice{
-		x \mapsto \OT{\mpar{s_{13}, s_3}}{\mpar{s'_{13}, s'_{3x}}}{\alpha_{13}}{\beta_{13j}^{j \in J'_{13x} \setminus \mbrc{k}} \uplus \beta_{3xj}^{j \in J'_{3x}}}{g_{13} \wedge g_{3x} \wedge \alpha_{3x} = \beta_{13k}}{\psi_{13} \uplus \psi_{3x}} & \text{if } k \in J'_{13} \\
-		x \mapsto \OT{\mpar{s_{13}, s_3}}{\mpar{s'_{13}, s_3}}{\alpha_{13}}{\beta_{13j}^{j \in J'_{13}}}{g_{13}}{\psi_{13}} & \text{otherwise}
-	} \]
-	We will prove \goal{0} for the family \(t_{31x}^{x \in X}\), the new goals are
-	\begin{gather}
-		\forall x \in X, J'_{31x} \cap H = J'_{21} \cap H \goal{0'} \\
-		V_{21} \uplus V_{31} \uplus \fvars{t_{21}} \vdash R\mpar{s_{21}, s_{31}} \wedge g_{21} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{21} = \alpha_{31x} \wedge \bigwedge_\subbox{j \in J'_{31x} \cap H} \beta_{21j} = \beta_{31xj} \\[12pt]
-			\nwedge g_{31x} \wedge R\mpar{s'_{21}, s'_{31x}}\psubst{\psi_{21} \uplus \psi_{31x}}
-		\end{array}} \goal{2}
-	\end{gather}
-\item[\goal{0'}:] Let \(x \in X\), by case on \(k \in J'_{12}\).
-	\begin{align*}
-		\text{If } k \in J'_{12}: && J'_{31x} \cap H & = \mpar{J'_{3x} \uplus J'_{13} \setminus \mbrc{k}} \cap \mpar{H_{23} \uplus J_1 \setminus \mbrc{k}} \\
-		&&& = \mpar{J'_{3x} \cap H_{23}} \uplus \mpar{J'_{12} \cap J_1} \setminus \mbrc{k} & \text{by } J'_{13} = J'_{12} \\
-		&&& = \mpar{J'_2 \cap H_{23}} \uplus \mpar{J'_{12} \cap J_1} \setminus \mbrc{k} & \text{by \hyp{1'}} \\
-		&&& = \mpar{J'_2 \uplus J'_{12} \setminus \mbrc{k}} \cap \mpar{H_{23} \uplus J_1 \setminus \mbrc{k}} \\
-		&&& = J'_{32} \cap H \\
-		\text{If } k \notin J'_{12}: && J'_{31x} \cap H & = \mpar{J'_{13} \setminus \mbrc{k}} \cap \mpar{H_{23} \uplus J_1 \setminus \mbrc{k}} \\
-		&&& = \mpar{J'_{12} \setminus \mbrc{k}} \cap \mpar{H_{23} \uplus J_1 \setminus \mbrc{k}} \\
-		&&& = J'_{32} \cap H
-	\end{align*}
-\item[\goal{2}:] Let \(\sigma: V_{21} \uplus V_{31} \uplus \fvars{t_{21}} \to \values\).
-	We use dummy values for the variables in \nmm{\biguplus_{x \in X} \fvars{t_{31x}}} to get the left side of the implication as an hypothesis (independent from these values):
-	\[ \sigma \vdash R\mpar{s_{21}, s_{31}} \wedge g_{21} \hyp{2} \]
-	If \(s_{12} \neq s_{13}\) then this hypothesis is \(\sigma \vdash \bot\), the empty family works and the proof is finished.
-	We can assume \(s_{12} = s_{13}\) and break \hyp{2} into
-	\begin{gather}
-		\sigma \vdash R_{23}\mpar{s_2, s_3} \hyp{2a} \\
-		\sigma \vdash \reach{A_{21}}\mpar{s_{21}} \hyp{2b} \\
-		\sigma \vdash \bigwedge_\subbox{v_1 \in V_1} v_{12} = v_{13} \hyp{2c} \\
-		\sigma \vdash g_{21} \hyp{2d}
-	\end{gather}
-	If \(k \in J'_{12}\), we use \hyp{1"} with valuation \(\sigma\) on variables \(V_2 \uplus V_3 \uplus \fvars{t_2}\), then we get the values of the implicit \(\exists\) in \nmm{\nu: \biguplus_{x \in X} \fvars{t_{3x}}}.
-	The left side of the implication is proved with \hyp{2a} and \hyp{2d}.
-	So we get a \(x \in X\) such that
-	\begin{gather}
-		\sigma \uplus \nu \vdash \alpha_2 = \alpha_{3x} \hyp{3a} \\
-		\sigma \uplus \nu \vdash \bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj} \hyp{3b} \\
-		\sigma \uplus \nu \vdash g_{3x} \hyp{3c} \\
-		\sigma \uplus \nu \vdash R_{23}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}} \hyp{3d}
-	\end{gather}
-	if \(k \notin J'_{12}\) we pose \(\nu \defobject \mbrc{}\) the empty valuation.
-	We extend the valuation \(\nu\) to cover the variables of \(t_{13}\) in \(t_{31x}\) using their value in \(t_{12}\), \(\nu' \defobject \nu \uplus \mset{v_{13} \mapsto \sigma\mpar{v_{12}}}{v_1 \in \fvars{t_1}}\)
-	We progress on \goal{2} by giving the valuation \(\sigma \uplus \nu'\) to the implicit \(\exists\), admitting the left side of the implication and choosing to prove the branch \(x\) of the disjunction:
-	\begin{gather}
-		\sigma \uplus \nu' \vdash \alpha_{21} = \alpha_{31x} \goal{3a} \\
-		\sigma \uplus \nu' \vdash \bigwedge_\subbox{j \in J'_{31x} \cap H} \beta_{21j} = \beta_{31xj} \goal{3b} \\
-		\sigma \uplus \nu' \vdash g_{31x} \goal{3c} \\
-		\sigma \uplus \nu' \vdash R\mpar{s'_{21}, s'_{31x}}\psubst{\psi_{21} \uplus \psi_{31x}} \goal{3d}
-	\end{gather}
-	Because composition doesn't change the produced actions nor its variables, \goal{3a} is proved by reflexivity.
-	\goal{3b} holds because the valuations for the actions of the holes in \(J_1\) coincide by definition of \(\nu'\) and by \hyp{3b} for the others (\(k \notin H\)).
-	For \goal{3c} we have two cases, if \(k \notin J'_{12}\) then \(g_{31x} \iff g_{13}\) and \hyp{2d} is sufficient (\(g_{21} \iff g_{13}\)), if \(k \in J'_{13}\) then \(g_{31x} \iff g_{13} \wedge g_{3x} \wedge \alpha_{3x} = \beta_{13k}\) so we also need \hyp{3c} and \hyp{3a} in addition to \hyp{2d} (\(g_{21} \iff g_{13} \wedge \alpha_2 = \beta_{12k}\)).
-	For \goal{3d} we first perform a tranfsformation.
-	\begin{align*}
-		& \sigma \uplus \nu' \vdash R\mpar{s'_{21}, s'_{31x}}\psubst{\psi_{21} \uplus \psi_{31x}} \\
-		\iff & \sigma \uplus \nu' \vdash \mpar{R_{23}\mpar{s'_2, s'_{3x}} \wedge \reach{A_{21}}\mpar{s'_{21}} \wedge \bigwedge_\subbox{v_1 \in V_1} v_{12} = v_{13}}\psubst{\psi_{12} \uplus \psi_2 \uplus \psi_{13} \uplus \psi_{3x}} \\
-		\iff & \sigma \uplus \nu' \vdash R_{23}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}} \wedge \reach{A_{21}}\mpar{s'_{21}}\psubst{\psi_{21}} \wedge \bigwedge_\subbox{v_1 \in V_1} \psi_{12}\mpar{v_{12}} = \psi_{13}\mpar{v_{13}} \\
-		\iff & \mpar{\sigma \uplus \nu \vdash R_{23}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}} \wedge \mpar{\sigma \vdash \reach{A_{21}}\mpar{s'_{21}}\psubst{\psi_{21}}} \wedge \mpar{\sigma \uplus \nu' \vdash \bigwedge_\subbox{v_1 \in V_1} \psi_{12}\mpar{v_{12}} = \psi_{13}\mpar{v_{13}}}
-	\end{align*}
-	The left side is \hyp{3d}.
-	For the middle part we use the preservation of reachability across transitions:
-	\[ \forall t_{21} \defobject \OTx{21}{}{21}{21} \in T_{21}, \fvars{t_{21}} \vdash \reach{A_{21}}\mpar{s_{21}} \wedge g_{21} \implies \reach{A_{21}}\mpar{s'_{21}}\psubst{\psi_{21}} \hyp{4} \]
-	\hyp{4} is used for transition \(t_{21}\) with valuation \(\sigma\), the left side of the implication is \hyp{2b} and \hyp{2d}.
-
-	For the right side, the variables of \(\psi_{12}\) and \(\psi_{13}\) are renaming of \(\psi_1\) on variables in \(\fvars{t_1}\) so proving the following is sufficient:
-	\[ \sigma \vdash \bigwedge_\subbox{v_1 \in V_1 \uplus \fvars{t_1}} v_{12} = v_{13} \goal{2d'} \]
-	Which holds by \hyp{2c} and by definition of \(\nu'\) for variables of the transition.
-\item[\goal{1}:] Let \nmm{\sigma: V_{21} \uplus V_{31} \uplus \biguplus_\subbox{t_{31} \in \fOT{s_{31}}} \fvars{t_{31}} \to \values}.
-	We use dummy values for the variables in \nmm{\biguplus_\subbox{t_{21} \in \fOT{s_{21}}} \fvars{t_{21}}} to get the left side of the implication (independent from these values), immediately broken into
-	\begin{gather}
-		\sigma \vdash R_{23}\mpar{s_2, s_3} \hyp{5a} \\
-		\sigma \vdash \reach{A_{21}}\mpar{s_{21}} \hyp{5b} \\
-		\sigma \vdash \bigvee_\subbox{t_{31} \in \fOT{s_{31}}} \fguard{t_{31}} \hyp{5c}
-	\end{gather}
-	\(R_{23}\) is a simulation and \(\reach{A_{21}}\) is a witness of the non-locking composition so we have the hypotheses:
-	\begin{gather}
-		V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash R_{23}\mpar{s_2, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{6} \\
-		V_{21} \uplus \biguplus_\subbox{t_{12} \in \fOT{s_{12}}} \fvars{t_{12}} \vdash \reach{A_{21}}\mpar{s_{21}} \wedge \bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}} \implies \bigvee_\subbox{t_{21} \in \fOT{s_{21}}} \fguard{t_{21}} \hyp{7}
-	\end{gather}
-	We use \hyp{6} with valuation \(\sigma\) to get \nmm{\nu: \biguplus_\subbox{t_{12} \in \fOT{s_{12}}} \fvars{t_{12}} \to \values}.
-	The left side of the implication is proved using \hyp{5a} and \hyp{5c} because the guards from transitions of \(A_3\) are still in transitions of \(A_{31}\), the right side gives:
-	\[ \sigma \uplus \nu \vdash \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \hyp{6'} \]
-	We then use \hyp{7} with valuation \(\sigma \uplus \nu\) to get \nmm{\nu': \biguplus_\subbox{t_{21} \in \fOT{s_{21}}} \fvars{t_{21}}}.
-	The left side of the implication is proved using \hyp{5b} and \hyp{6'}, the right side gives:
-	\[ \sigma \uplus \nu' \vdash \bigvee_\subbox{t_{21} \in \fOT{s_{21}}} \fguard{t_{21}} \hyp{7'} \]
-	\goal{1} is proved for valuation \(\nu'\) by admitting the left side and using \hyp{7'}.
-\end{proof}
-\begin{thm}[FH-bisimulation compatibility] Open automata refinement is compatible with FH-bisimulation \end{thm}
-\begin{proofsketch} The requirements of FH-bisimulation are strictly stronger than the open automata refinement so using transitivity is sufficient. \end{proofsketch}
-With that last property, every interesting property is proved for the presented refinement relation.
+\section{Properties}\label{sec:prop}
+\TODO{1.5 pages}
 
 \section{Conclusion}\label{sec:ccl}
-In this report we redefined on open automata an operation from open pNets called composition.
-This operation was defined as the composition of the open pNets used to generate the open automata and not directly on open automata.
-So to reason on composition directly and to better separate the models the definition had to be given without introducing open pNets.
-Then we recalled the main properties expected from a refinement relation on a structure with composition and adapted them to open automata.
-To do that we restricted the composition so that it doesn't introduce deadlocks.
-Then we introduced several refinement relations in restricted cases to avoid dealing immediately with the hard issue of the incomparability of hole sets.
-Finally we introduced a refinement relation having all the interesting properties and dealing with the aforementioned issue at the cost of a slight modification on transitivity.
+\TODO{0.5 pages}
 
-However the refinement presented here still do not work on the motivating example because of silent actions.
-To be able to refine in the presence of silent action, a weak variant of the simulation is needed.
-This variant will also probably be able to encompass action refinement as a valid refinement because the mechanism are similar.
-
-\pagebreak
-\bibliographystyle{plain}
+ \bibliographystyle{splncs04}
  \bibliography{biblio}

### 2021-07-07 2021-Refinement/paper/refinementarticle.tex
TL figs
notations

@@
 
+This section presents the notations we used and the principles of automata.
+Except for minor changes in the notations, the only new contribution of this section is the definition of a composition operator for open automata.
+%
+%Notations will be defined with the operator \(\defnotation\) and names are given with the operator \(\defobject\) as follows:
+%\begin{align*}
+%	\mathit{notation\_with\_variables} & \defnotation \mathit{notated\_object\_using\_the\_variables} \\
+%	\mathit{name} & \defobject \mathit{fully\_defined\_mathematical\_object}
+%\end{align*}
+
+%Throughout this paper, tuples will be noted differently depending on what they represent.
+%This helps distinguishing the manipulated objects.
+%Every such notation will be introduced in the definition of the object.
+
+Families of values, or equivalently maps will be noted \(\mset{i \mapsto x_i}{i \in I}\), \(\mset{i \gets x_i}{i \in I}\) or \(x_i^{i \in I}\).
+% TODO: introduire le fait que \exists c_j^{j \in J} défini J et {j \mapsto c_j}
+%For instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\).
+%They will be used depending on what is more convenient.
+%For instance \(\mbrc{\alpha \mapsto 1, \beta \mapsto 2, \gamma \mapsto 3}\) has no simple generating expression and is better represented with the finite version of first notation.
+The disjoint union on set is noted \(\uplus\)\footnote{\(\uplus\) notation either supposes that the sets are disjoint or rename conflicting objects depending on the context}.
+Disjoint union is also used on maps.
+%There are several ways of ensuring a union is disjoint, we will indifferently either suppose sets are disjoint or rename conflicting object (useful for variables).
+%The disjoint union of two maps \(\varphi: I \to X\) and \(\psi: J \to Y\) with \(I \cap J = \emptyset\) is noted \(\varphi \uplus \psi\) and has the following signature \(I \uplus J \to X \cup Y\).
+In a formula, a quantifier followed by a finite set will be used as a shorthand for the quantification on every variable in the set:
+\(\forall \mbrc{a_1, \dots, a_n}, \exists \mbrc{b_1, \dots, b_m}, P\) means \(\forall a_1, \dots, \forall a_n, \exists b_1, \dots, \exists b_m, P\).
+
+\begin{figure}
+\centering
+\input{Traffic_Lights_Controller.tex}
+\vrule
+\input{Traffic_Lights_Full.tex}
+\caption{TL}
+\label{fig:TL}
+\end{figure}
+
 \section{A First Refinement Relation}\label{sec:refinement}

### 2021-07-09 2021-Refinement/paper/refinementarticle.tex
a bit of notations

@@
 
-\usepackage{amsmath}
+\usepackage{amsmath,amssymb}
 %\usepackage{amsthm}
@@
 
+\begin{definition}[Expression algebra, Action algebra, Formulas, Terms]
+An expression algebra \(E\) is the disjoint union  of  terms,  actions, and  formulas
+\( E=\terms \uplus \actions \uplus \formulas\) .
+\(\terms\) and \(\actions\) are term algebras.
+The formulas \(\formulas\) contain at least first order formulas and equality\footnote{Equality does not need to be only syntactic.} over \(\terms\) and \(\actions\).
+\end{definition}
+
+ \(\fvars{e}\) is the set of variables in \(e \in E\) that are not bound by any binder. An expression is closed if \(\fvars{e}=\emptyset\).
+% The expressions restricted to variables in \(V\) are \(E_V := \mset{e \in E}{\fvars{e} \subseteq V}\).
+%\defitem The closed expressions are expressions restricted to variables in \(\emptyset\), \(E_\emptyset\).
+
+\TODO{on a besoin de quoi dans la suite?}
+
+\begin{definition}[Values, Satisfiability, (Parallel) substitution]
+We assume that the following are given:
+
+$\bullet$ The values \(\values\), which are interpretations of closed terms.
+
+$\bullet$ The satisfiability relation on closed formulas, \({\vdash} f\) where \(f \in \rformulas\).
+
+$\bullet$ The substitution in \(e \in E\) of \(x \in \fvars{e}\) by \(t \in \terms\), \(e\subst{t}{x}\).
+
+$\bullet$ The parallel substitution in \(e \in E\) of variables in \(V\) by \(\psi: V \to \terms\), \(e\psubst{\psi}\).
+\end{definition}
+For the parallel substitution, the set \(V\) is not required to be a subset of \(\fvars{e}\).
+In the case it isn't, the variables in \(V \setminus \fvars{e}\) are not substituted.
+The substitutions might give a ill-formed expression; for instance let the terms be integers and pairs with (pointwise) addition, \(\mpar{a + b}\psubst{a \mapsto 7, b \mapsto \mpar{4, 5}}\) is a ill-formed term.
+This can be guarded with the check \(e\subst{t}{x} \in E\) and \(e\psubst{\psi} \in E\) and it will implicitly be the case, for instance when there is quantification on \(t\) and \(\psi\), to simplify notations.
+
+The interpretation of terms is supposed to be decidable.
+The satisfiability of formulas might not be decidable nor complete nor consistent,
+but we will consider in the following that they are; this can be achieved by restricting the term algebra to a decidable subset.
+For instance a formula with quantifiers on variables might not be provable even if it is true for all values of these variables.
+In practice the formulas will be given to a SMT solver and we cannot always make sure they have all the previous properties but, at least any property found satisfiable by the SMT is ensured to be true.
+\(\vdash\) can hence be interpreted as an indicator of what is given to the SMT; it separates the external logic and the logic on \(\formulas\).
+
+\subsection{Open Automata}\label{sec:def}
+
 \begin{figure}

### 2021-07-12 2021-Refinement/paper/refinementarticle.tex
first rough version of an abstract .

@@
 150--250 words.
+
+Establishing equivalences and refinement relations between programs is an important mean for 
+verifying the correctness of programs, by formaly proving the relation between a specification and an implementation, 
+proving that two implementation are equivalent, or justifying optimisations and transformations, by establishing that the
+behaviors of a modified program simulate those of to the source one.
+
+In this article, we discuss a notion of refinement between so-called "open automata", which are symbolic
+behavioral models for communicationg systems. Open automata may have "holes" modeling elements of their
+context, and can be composed by instanciation of the holes. This allows for a compositional approach for
+verification of their behavior, essential to address proofs about large realistic systems.
+
+We define several varriants of refinement between systems including either equal or different sets of holes, and 
+show under which conditions these refinements are preserved by composition of open automata. We also discuss
+the relations between these refinements and the existence of deadlocks.
+We iluustrate these notions on several simple use-cases.
 

### 2021-07-19 2021-Refinement/paper/refinementarticle.tex
Finally reached the end of base notations

--- 2021-07-07 2021-Refinement/paper/refinementarticle.tex
@@
 
+%\begin{definition}[Expression algebra, Action algebra, Formulas, Terms]
+An expression algebra \(E\) is the disjoint union  of  terms,  actions, and  formulas
+\( E=\terms \uplus \actions \uplus \formulas\) .
+\(\terms\) and \(\actions\) are term algebras.
+The formulas \(\formulas\) contain at least first order formulas and equality\footnote{Equality does not need to be only syntactic.} over \(\terms\) and \(\actions\).
+%\end{definition}
+
+ \(\fvars{e}\) is the set of variables in \(e \in E\) that are not bound by any binder. An expression is closed if \(\fvars{e}=\emptyset\).
+The set \(\values\) denote values which is a subset of closed terms.
+
+The substitution in \(e \in E\) of \(x \in \fvars{e}\) by \(t \in \terms\), is denoted \(e\subst{t}{x}\), and its generalisation to the parallel substitution of variables in \(V\) by \(\psi: V \to \terms\) is denoted \(e\psubst{\psi}\).
+
+ We suppose given a decidable satisfiability relation on formulas, \({\vdash} f\) is the satisfiability over closed formulas.
+% In practice one of our objective is to be able to use a SMT solver to reason automatically on the properties of open automata, in this case
+%\(\vdash\) can hence be interpreted as an indicator of what is given to the SMT; it separates the external logic and the logic on \(\formulas\).
+We will  use two satisfiability relations:
+\begin{itemize}
+\item The satisfiability of a formula \(f \in \formulas\) under some valuation \(\sigma: V \to \values\):
+\( \sigma \vdash f ::= \vdash \exists \fvars{f\psubst{\sigma}}, f\psubst{\sigma} \)
+\item The satisfiability of a formula \(f \in \formulas\) with some variable set \(V\) as context:
+\( V \vdash f ::=  \vdash \forall V, \exists\mpar{\fvars{f} \setminus V}, f \)
+\end{itemize}
+
+%For instance a formula with quantifiers on variables might not be provable even if it is true for all values of these variables.
+
+\subsection{Open Automata}\label{sec:def}
+
 \begin{figure}

### 2021-07-19 2021-Refinement/paper/refinementarticle.tex
open automata def

@@
 
+\begin{definition}[Open automaton]
+An open automaton is a tuple \(\OAg\) with \(S\) the set of states, \(s_0 \in S\) the initial state, \(V\) the finite set of variable names, \(\sigma_0: V' \to \values\) the initial valuation of variables where \(V' \subseteq V\), \(J\) the set of hole names and \(T\) the set of open transitions.
+A pair of a state and a valuation is called a configuration.
+\end{definition}
+We suppose that each automaton has a distinct set of variables. If there is a clash of variable names we suppose that there is still a way to  distinguish them.
+
+%%% LUDO STOPPED HERE
+
+\begin{definition}[Open transition, Instanciated transition]
+An open transition is a tuple \nmm{\OTg} with \(s, s' \in S\) the source and target states, \(\alpha \in \actions\) the produced action, \(J' \subseteq J\) the holes involved in the transition, \(\beta_j \in \actions\) the actions of the holes, \(g \in \formulas\) the guard and \(\psi: V \to \terms\) the variable assignments.
+An open transition can have many unbound variables.
+
+An instanciated transition of the automaton is transition produced by any well-formed substitution of the unbound variables of the transition minus the automaton variables.
+\end{definition}
+The intuition of an open automaton is a partially defined LTS with variables, guards on transitions, and parametrised actions.
+The LTS is partial in the sense that one can plug an LTS in the hole and the surrounding LTS will react to the actions emitted by the sub-LTS put in the hole.
+Initially the automaton is in the initial state with an extension on all the variables of the initial valuation.
+In any configuration, it can perform instanciated transitions which source state is the current state and which guard is satisfiable in the current valuation if the holes emit the indicated actions.
+An instanciated transition is a transition where every variable that is not an automaton variable is instantiated with a value.
+By performing the instanciated transition, the automaton emits the indicated action and updates its configuration according to the target state and variable assignments.
+
 \begin{figure}
@@
 
+\section{a recuperer si on se rend comtpte que c'est utile}
+When we will introduce refinements in Section \ref{sec:prelref}, setting an undefined variable will be considered a valid refinement, for instance a \(5\) bits register is a particular \(n\) bits register.
+
  \bibliographystyle{splncs04}

### 2021-07-19 2021-Refinement/paper/refinementarticle.tex
example

@@
 \usepackage{hyperref}
+\usepackage{nccrules}
 \AtBeginDocument{\renewcommand\setminus{\smallsetminus}}
@@
 Establishing equivalences and refinement relations between programs is an important mean for 
-verifying the correctness of programs, by formaly proving the relation between a specification and an implementation, 
+verifying the correctness of programs, by formally proving the relation between a specification and an implementation, 
 proving that two implementation are equivalent, or justifying optimisations and transformations, by establishing that the
@@
 In this article, we discuss a notion of refinement between so-called "open automata", which are symbolic
-behavioral models for communicationg systems. Open automata may have "holes" modeling elements of their
+behavioral models for communicating systems. Open automata may have "holes" modeling elements of their
 context, and can be composed by instanciation of the holes. This allows for a compositional approach for
@@
 
-We define several varriants of refinement between systems including either equal or different sets of holes, and 
+We define several variants of refinement between systems including either equal or different sets of holes, and 
 show under which conditions these refinements are preserved by composition of open automata. We also discuss
 the relations between these refinements and the existence of deadlocks.
-We iluustrate these notions on several simple use-cases.
+We illustrate these notions on several simple use-cases.
 
@@
 Here the refinement relation does not consider action refinement as valid but it should be done in future work.
-Also they check how LTL properties are preserved or combined using ther refinement which we do not do.
+Also they check how LTL properties are preserved or combined using their refinement which we do not do.
 However their model is less expressive: the transition system model is less expressive than open automata and the parallel composition is less expressive than composition on open automata.
@@
 Their relation additionally prevents deadlock and livelocks.
-The compositon is also extended to synchronised composition which is more expressive.
+The composition is also extended to synchronised composition which is more expressive.
 In our work we also deal with deadlocks but not with livelocks since the latter arise only with silent actions.
@@
 
+As an example, the traffic light system  that controls  
+ traffic at the intersection of a busy highway. In Figure \ref{fig:tls} we model it as open automaton and abstract the timer   as  Holes: a controller and a counter.
+
 \begin{figure}
 \centering
+\input{Traffic_Lights_Spec.tex}
+\caption{The specification of a traffic light system}
+\label{fig:tls}
+\end{figure}
+
+\begin{figure}
+%\centering
 \input{Traffic_Lights_Controller.tex}
-\vrule
+\input{Traffic_Lights_Register.tex}
+\caption{On the left: An example of controller agent; On the right: An example of counter agent}
+\label{fig:tlh}
+\end{figure}
+
+This example is derived and adapted from a traffic light controller in a collection of examples for pNets.
+It is supposed to be a single traffic light.
+
+\begin{figure}
+\centering
 \input{Traffic_Lights_Full.tex}
-\caption{TL}
-\label{fig:TL}
+\caption{The full traffic lights system}
+\label{fig:tlf}
 \end{figure}

### 2021-07-20 2021-Refinement/paper/refinementarticle.tex
automata definition

@@
 \subsection{Open Automata}\label{sec:def}
+ Open automata are labelled transition systems with variables  that can be used to compose other automata: they are made of transitions that are dependent of the actions of ``holes'', a composition operation consists in filling a hole with another automaton to obtain a more complete automaton.
+The variables makes the automata symbolic, and the holes allow for a partial definition of the behaviour.
 
-\begin{definition}[Open automaton]
-An open automaton is a tuple \(\OAg\) with \(S\) the set of states, \(s_0 \in S\) the initial state, \(V\) the finite set of variable names, \(\sigma_0: V' \to \values\) the initial valuation of variables where \(V' \subseteq V\), \(J\) the set of hole names and \(T\) the set of open transitions.
-A pair of a state and a valuation is called a configuration.
+\begin{definition}[Open transition, Open automaton]
+An \emph{open automaton} is a tuple \(\OAg\) with \(S\) the set of states, \(s_0 \in S\) the initial state, \(V\) the finite set of variable names, \(\sigma_0: V' \to \values\) the initial valuation of variables where \(V' \subseteq V\), \(J\) the set of hole names and \(T\) the set of open transitions.
+
+An \emph{open transition} is a tuple \nmm{\OTg} with \(s, s' \in S\) the source and target states, \(\alpha \in \actions\) the produced action, \(J' \subseteq J\) the holes involved in the transition, \(\beta_j \in \actions\) the actions of the holes, \(g \in \formulas\) the guard and \(\psi: V \to \terms\) the variable assignments.
 \end{definition}
-We suppose that each automaton has a distinct set of variables. If there is a clash of variable names we suppose that there is still a way to  distinguish them.
 
-%%% LUDO STOPPED HERE
+The following terminology will be used to reason on open automata
+\begin{definition}[Configuration, instantiated transition]
+A pair of a state and a valuation is called a \emph{configuration}.
+An \emph{instantiated transition} of an automaton \(\OAg\) is a transition  \(t\psi\) where $t\in T$ and $\psi$ is a  well-formed substitution of the unbound variables of $t$  minus the automaton variables $V$.
+\end{definition}
 
-\begin{definition}[Open transition, Instanciated transition]
-An open transition is a tuple \nmm{\OTg} with \(s, s' \in S\) the source and target states, \(\alpha \in \actions\) the produced action, \(J' \subseteq J\) the holes involved in the transition, \(\beta_j \in \actions\) the actions of the holes, \(g \in \formulas\) the guard and \(\psi: V \to \terms\) the variable assignments.
-An open transition can have many unbound variables.
+\paragraph{Open automaton composition}
 
-An instanciated transition of the automaton is transition produced by any well-formed substitution of the unbound variables of the transition minus the automaton variables.
-\end{definition}
-The intuition of an open automaton is a partially defined LTS with variables, guards on transitions, and parametrised actions.
-The LTS is partial in the sense that one can plug an LTS in the hole and the surrounding LTS will react to the actions emitted by the sub-LTS put in the hole.
-Initially the automaton is in the initial state with an extension on all the variables of the initial valuation.
-In any configuration, it can perform instanciated transitions which source state is the current state and which guard is satisfiable in the current valuation if the holes emit the indicated actions.
-An instanciated transition is a transition where every variable that is not an automaton variable is instantiated with a value.
-By performing the instanciated transition, the automaton emits the indicated action and updates its configuration according to the target state and variable assignments.
+TODO
+
+\paragraph{A bisimulation for open automata}
+
+TODO
+
+\subsection{Example}
 

### 2021-07-21 2021-Refinement/paper/refinementarticle.tex
part of example

@@
 As an example, the traffic light system  that controls  
- traffic at the intersection of a busy highway. In Figure \ref{fig:tls} we model it as open automaton and abstract the timer   as  Holes: a controller and a counter.
+ traffic at the intersection of a busy highway. The open automaton  
+modeling this system  is illustrated in  Figure \ref{fig:tls}. This automaton has three states  remembering which coloured light
+is on (Red, Yellow or Green).
+It includes two holes: a controller ($\symb{ctl}$) and a counter ($\symb{cnt}$)  depicting together the behaviour of the timer.
+The color switches when the counter and the controller component agree that the time is over.
+The new time limit can be set by the counter component and the exposed action to the environment is an unobservable  action $\tau$.
+
+The open automata shown in Figure  \ref{fig:ctlandcnt} models  the timer.
+On the left, the controller component designed to be connected in the hole $\symb{ctl}$.
+Its role is to decide the duration before switching the lights.
+We control the time interval for each light by setting them by prior knowledge:  17s for the first duration, 3s for the second, and 20s for the third.
+On the right, the tick counter component designed to be connected in the hole $\symb{cnt}$.
+It measures elapsed model time in ticks by counting ticks until the time limit retrieved beforehand is reached, then emits an over action with the elapsed time and restart.
+
+In Figure \ref{fig:tlf} we present the composition of the three automata.
+Each state of the result of the composition consists  of  a state of traffic light system together with a state of controller component and one of counter component.
 
@@
 \input{Traffic_Lights_Spec.tex}
-\caption{The specification of a traffic light system}
+\caption{The specification of a Traffic Light system}
 \label{fig:tls}
@@
 \input{Traffic_Lights_Register.tex}
-\caption{On the left: An example of controller agent; On the right: An example of counter agent}
-\label{fig:tlh}
+\caption{(a) An example of controller component ~~  (b) An example of counter component}
+\label{fig:ctlandcnt}
 \end{figure}
-
-This example is derived and adapted from a traffic light controller in a collection of examples for pNets.
-It is supposed to be a single traffic light.
 
@@
 \input{Traffic_Lights_Full.tex}
-\caption{The full traffic lights system}
+\caption{The full Traffic Lights system}
 \label{fig:tlf}

### 2021-07-23 2021-Refinement/paper/refinementarticle.tex
nop
Example comments

@@
 On the right, the tick counter component designed to be connected in the hole $\symb{cnt}$.
-It measures elapsed model time in ticks by counting ticks until the time limit retrieved beforehand is reached, then emits an over action with the elapsed time and restart.
 
@@
 Each state of the result of the composition consists  of  a state of traffic light system together with a state of controller component and one of counter component.
+The composed automaton  takes over  the same steps as the traffic light automaton but it also includes new steps,  indicting the change of states for the setting of timer.
+Its $\tau$ transitions involve both the traffic light automaton and the hole  automata, they correspond to  a joint step of  sending time thresholds of the controller, the time setting of the counter.
+For instance, the  $\tau$  transition starting from \(R1S\), it is obtained by composition of both
+\nmm{\OT{R}{R}{\tau}{\mbrc{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}, \nmm{\OT{1}{2}{\theta\mpar{17}}{\mbrc{}}{\top}{\mbrc{}}} and   \nmm{\OT{S}{C}{\act{set}\mpar{x}}{\mbrc{}}{\top}{\mbrc{t \gets x, c \gets 0}}}.
+\\ However, the joint composition of  \nmm{\OT{R}{R}{\tau}{\mbrc{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}, \nmm{\OT{2}{3}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} and
+\nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} is not agreed because it would produce a transition whose guard is not satisfiable, i.e., \nmm{\OT{R2C}{R3C}{\tau}{\mbrc{}}{\top \wedge \top \wedge c < t \wedge \act{set}\mpar{x} = \act{tick} \wedge \theta\mpar{x} = \delta\mpar{x}}{\mbrc{c \gets c + 1}}}.
 

### 2021-07-23 2021-Refinement/paper/refinementarticle.tex
initial push: composition

--- 2021-07-21 2021-Refinement/paper/refinementarticle.tex
@@
 
+\TODO{useful or not?}
+\begin{definition}[Guard, Out-transition, Transition variables]
+Let \(V\) be the variable names of the considered automaton, \(T\) its transitions and \(r\) one of its states.
+\(\fOT[T]{r} \in T\) are called the out-transitions of the state \(r\).
+\(\fIT[T]{r} \in T\) are called the in-transitions of the state \(r\).
+When the transition set is clear from the context, it will be omitted.
+The local variables of a transition \(\fvars{t}\) are all variables appearing in transition \(t\) except the global variables of the automaton.
+\begin{align*}
+	\fOT[T]{r} & ::= \mset{\OTg \in T}{s = r} &
+	\fIT[T]{r} & ::= \mset{\OTg \in T}{s' = r} \\
+\end{align*}
+\vspace{-1cm}
+\begin{gather*}
+	\fguard{\OTg} ::= g \\
+	\fvars{\OTg} ::= \mpar{\fvars{\alpha} \cup \fvars{g} \cup \bigcup_{j \in J'} \fvars{\beta_j} \cup \bigcup_{v \in V} \fvars{\psi\mpar{v}}} \setminus V
+\end{gather*}
+\end{definition}
+
 \paragraph{Open automaton composition}
+
+Open automata are partially specified automata, that partiality comes mostly from the holes.
+A hole is an interface in which we can plug an open automaton.
+The plugging operation is called composition.
+The composition of open automata was already implicitly defined by the means of composition on pNets in previous work \cite{henrio:01299562} but never completely formalised on open automata.
+The definition of composition below is a direct translation of what happens with pNets composition without the need of introducing pNets.
+\begin{definition}[Composition of open automata]
+The composition of \(A_c = \OAg[c]\) in the hole \(k \in J_p\) of \(A_p = \OAg[p]\) gives the open automaton defined as follows.
+\begin{align*}
+	A_p\subst{A_c}{k} ::= & \OA{S_p \times S_c}{\mpar{s_{0p}, s_{0c}}}{V_p \uplus V_c}{\sigma_{0p} \uplus \sigma_{0c}}{J_c \uplus J_p \setminus \mbrc{k}}{T} \\
+	\text{with } T = & \mset{\OT{\mpar{s_p, s_c}}{\mpar{s'_p, s'_c}}{\alpha_p}{\beta_j^{j \in J'_c \uplus J'_p \setminus \mbrc{k}}}{g_p \wedge g_c \wedge \alpha_c = \beta_k}{\psi_p \uplus \psi_c}}{\OTx{p}{}{}{p} \in T_p, \OTx{c}{}{}{c} \in T_c} \\
+	& \cup \mset{\OT{\mpar{s_p, s_c}}{\mpar{s'_p, s_c}}{\alpha_p}{\beta_j^{j \in J'_p}}{g_p}{\psi_p}}{\OTx{p}{}{}{p} \in T_p, k \notin J'_p, s_c \in S_c}
+\end{align*}
+\end{definition}
+The action emitted when \(A_c\) makes a transition is synchronised with the action of the hole \(k\) in transitions of \(A_p\) which have it as a hole action (first transition set, \(\alpha_c = \beta_k\)).
+The composition may look like a handshake, with both automata running in parallel (product of states and joint variables) however it is asymmetric:
+The first automaton decides when the second can evolve by involving it in a transition, while the first automaton can evolve independently as soon as the hole is not involved in an open transition.
 
@@
 
-TODO
+TODO OR NOT?
 
 \subsection{Example}
-
+\newcommand\symb[1]{\TODO{#1}}
 As an example, the traffic light system  that controls  

### 2021-07-23 2021-Refinement/paper/refinementarticle.tex

--- 2021-07-23 2021-Refinement/paper/refinementarticle.tex
@@
 
+\TODO{useful or not?}
+\begin{definition}[Guard, Out-transition, Transition variables]
+Let \(V\) be the variable names of the considered automaton, \(T\) its transitions and \(r\) one of its states.
+\(\fOT[T]{r} \in T\) are called the out-transitions of the state \(r\).
+\(\fIT[T]{r} \in T\) are called the in-transitions of the state \(r\).
+When the transition set is clear from the context, it will be omitted.
+The local variables of a transition \(\fvars{t}\) are all variables appearing in transition \(t\) except the global variables of the automaton.
+\begin{align*}
+	\fOT[T]{r} & ::= \mset{\OTg \in T}{s = r} &
+	\fIT[T]{r} & ::= \mset{\OTg \in T}{s' = r} \\
+\end{align*}
+\vspace{-1cm}
+\begin{gather*}
+	\fguard{\OTg} ::= g \\
+	\fvars{\OTg} ::= \mpar{\fvars{\alpha} \cup \fvars{g} \cup \bigcup_{j \in J'} \fvars{\beta_j} \cup \bigcup_{v \in V} \fvars{\psi\mpar{v}}} \setminus V
+\end{gather*}
+\end{definition}
+
 \paragraph{Open automaton composition}
 
-TODO
+Open automata are partially specified automata, that partiality comes mostly from the holes.
+A hole is an interface in which we can plug an open automaton.
+The plugging operation is called composition.
+The composition of open automata was already implicitly defined by the means of composition on pNets in previous work \cite{henrio:01299562} but never completely formalised on open automata.
+The definition of composition below is a direct translation of what happens with pNets composition without the need of introducing pNets.
+\begin{definition}[Composition of open automata]
+The composition of \(A_c = \OAg[c]\) in the hole \(k \in J_p\) of \(A_p = \OAg[p]\) is the open automaton defined as follows.
+\[
+	A_p\subst{A_c}{k} ::=  \OA{S_p \times S_c}{\mpar{s_{0p}, s_{0c}}}{V_p \uplus V_c}{\sigma_{0p} \uplus \sigma_{0c}}{J_c \uplus J_p \setminus \mbrc{k}}{T} \]
+
+\begin{align*}
+	\text{with } T = & \mset{\OT{\mpar{s_p, s_c}}{\mpar{s'_p, s'_c}}{\alpha_p}{\beta_j^{j \in J'_c \uplus J'_p}}{g_p \wedge g_c \wedge \alpha_c = \beta_k}{\psi_p \uplus \psi_c}}{ \OT{s_p}{s'_p}{\alpha_p}{\beta_j^{j \in J'_p \uplus \mbrc{k} }}{g_p}{\psi_p} \in T_p, \OTx{c}{}{}{c} \in T_c} \\
+	& \cup \mset{\OT{\mpar{s_p, s_c}}{\mpar{s'_p, s_c}}{\alpha_p}{\beta_j^{j \in J'_p}}{g_p}{\psi_p}}{\OTx{p}{}{}{p} \in T_p, k \notin J'_p, s_c \in S_c}
+\end{align*}
+\end{definition}
+The first automaton decides when the second can evolve by involving its hole in a transition:
+The action emitted when \(A_c\) makes a transition is synchronised with the action of the hole \(k\) in transitions of \(A_p\) .
 

### 2021-07-23 2021-Refinement/paper/refinementarticle.tex
sat

@@
 \begin{itemize}
-\item The satisfiability of a formula \(f \in \formulas\) under some valuation \(\sigma: V \to \values\):
+\item The satisfiability of a formula \(f \in \formulas\) under some valuation \(\sigma: V \to \values\) is defined as follows:
 \( \sigma \vdash f ::= \vdash \exists \fvars{f\psubst{\sigma}}, f\psubst{\sigma} \)
-\item The satisfiability of a formula \(f \in \formulas\) with some variable set \(V\) as context:
+\item The satisfiability of a formula \(f \in \formulas\) with some variable set \(V\) as context is defined as follows:
 \( V \vdash f ::=  \vdash \forall V, \exists\mpar{\fvars{f} \setminus V}, f \)
@@
 \section{A First Refinement Relation}\label{sec:refinement}
+
+deadlock and reachability
+
+Hole - = relation
+
 \TODO{4 pages}

### 2021-07-26 2021-Refinement/paper/refinementarticle.tex
un peu de biblio

--- 2021-07-23 2021-Refinement/paper/refinementarticle.tex
@@
 
+\newcommand{\symb}[1]{\makebox{\it #1}}
 \input{common.tex}
@@
 %
-\authorrunning{Rabéa Ameur-Boulifa et al.}
+\authorrunning{Rab\'ea Ameur-Boulifa et al.}
 % First names are abbreviated in the running head.
@@
 \begin{abstract}
- The abstract should briefly summarize the contents of the paper in
-150--250 words.
+\TODO{ The abstract should briefly summarize the contents of the paper in 150--250 words.}
 
@@
 \TODO{1 page}
+
+The notion of refinement aims of capturing the relation between  a specification and an implementation of the same component.
+It is usually defined as trace inclusion or simulation \cite{Milner:1980}; this ensures that all behaviours of the implementation must be also behaviours of the specification.
+This definition, which is based on systems whose behaviour is fully defined, is not well-suited for open systems  as it requires to reason also about unspecified behaviours.
+
+There are some works that have been interested in the  the refinement of open systems.
+
+The definition of refinement for open systems in terms of alternating simulation \cite{Alur:1998} and \cite{deAlfaro:2021} is originating  from the game theory \cite{deAlfaro:2003}.
 
@@
 \subsection{Example}
-\newcommand\symb[1]{\TODO{#1}}
+
 As an example, the traffic light system  that controls  
@@
 \nmm{\OT{R}{R}{\tau}{\mbrc{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}, \nmm{\OT{1}{2}{\theta\mpar{17}}{\mbrc{}}{\top}{\mbrc{}}} and   \nmm{\OT{S}{C}{\act{set}\mpar{x}}{\mbrc{}}{\top}{\mbrc{t \gets x, c \gets 0}}}.
-\\ However, the joint composition of  \nmm{\OT{R}{R}{\tau}{\mbrc{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}, \nmm{\OT{2}{3}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} and
-\nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} is not agreed because it would produce a transition whose guard is not satisfiable, i.e., \nmm{\OT{R2C}{R3C}{\tau}{\mbrc{}}{\top \wedge \top \wedge c < t \wedge \act{set}\mpar{x} = \act{tick} \wedge \theta\mpar{x} = \delta\mpar{x}}{\mbrc{c \gets c + 1}}}.
+\\
+However, the joint composition of transitions  \nmm{\OT{R}{R}{\tau}{\mbrc{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}, \nmm{\OT{2}{3}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} and
+\nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} is not agreed because it would produce a transition whose guard is not satisfiable.
+It will produce the following transition: \nmm{\OT{R2C}{R3C}{\tau}{\mbrc{}}{\top \wedge \top \wedge c < t \wedge \act{set}\mpar{x} = \act{tick} \wedge \theta\mpar{x} = \delta\mpar{x}}{\mbrc{c \gets c + 1}}}.
 

### 2021-07-26 2021-Refinement/paper/refinementarticle.tex
work on deadlocks

--- 2021-07-23 2021-Refinement/paper/refinementarticle.tex
@@
 
-\usepackage{amsmath,amssymb}
+\usepackage{amsmath,amssymb,mathabx}
 %\usepackage{amsthm}
@@
  \(\fvars{e}\) is the set of variables in \(e \in E\) that are not bound by any binder. An expression is closed if \(\fvars{e}=\emptyset\).
-The set \(\values\) denote values which is a subset of closed terms.
+The set \(\values\) denote values which is a subset of closed terms. \(\rformulas[V]\) is the set of formulas $f$ that only use variables in $V$, i.e. the formulas such that  \(\fvars{f}\subseteq V\).
 
@@
 
-deadlock and reachability
+Similarly to FH-bisimulation we are interested here in finding relations between states of to open automata that contain variables and holes.
+However here we want to biuld a refinement relation that is a simulation but also guarantees that no deadlock is introduced.
+Our objective is to characterize when a relation between two states of two open automata have the desired property.
+Such a relation has the following signature: \( S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
+We first define when a relations is deadlock reducing, before characterising a first simple refinement relation only valid to compare automata with identical holes.
+
+\begin{definition}[Deadlock reduction]\label{def:dpwd}
+A relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if  it satisfies the following:
+\[ \forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \]
+\end{definition}
+
+Unfortunately, in the general case, this property is conflicting with the properties about the relation on automata because every property involving composition would be applicable on composition introducing deadlocks.
+
+\subsection{Issue with deadlock reduction and composition}
+A way to solve the conflict between deadlock reduction and the properties involving composition is to only consider a composition that do not introduce deadlocks.
+With this new condition on validity of composition we are able to define in the next sections a refinement relation where most of the properties of interest are satisfied.
+
+Before characterising a composition which does not introduce deadlocks we need to be able to tell which states are reachable because some deadlocks are not reachable and should not be considered as being introduced.
+\begin{definition}[Reachability]
+For any open automata \(A = \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is a predicate on states satisfying both
+
+ Inital state is reachable: \(\sigma_0 \vdash \reach{A}\mpar{s_0}\)
+
+ Reachability is preserved across transitions: \nmm{\forall t = \OTg \in T, \fvars{t} \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}}
+\end{definition}
+The reachability predicate is used to characterise the reachable configurations in a run of an automaton.
+In fact the role of the predicate is to characterise potentially reachable configurations without having to characterise configurations as the result of a valid path in an automaton.
+
+To do that we impose that the initial configuration is reachable and that reachability is preserved by taking valid transitions.
+This effectively makes reachability take into account all paths, and potentially over-approximate the reachable configurations.
+The exact reachability may not be representable in the formulas, hence the need of potentially over-approximating.
+\begin{definition}[Non-locking composition, intuitive definition]
+Let \(A_i = \OAg[i], 0 \leq i \leq n\).
+The composition \(A = A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is non-locking if \(A\) has a reachability predicate satisfying:
+From reachable configurations, if there was a possible transition in \(A_0\) then there is a possible transition in \(A\).
+Formally for \(\OAg = A\), it gives
+\begin{multline*}
+	\forall s = \mpar{s'_i}_{0 \leq i \leq n} \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A}\mpar{s}} \implies \\
+	\mpar{\exists t_0 \in \fOT{s'_0}, \exists \nu_0: \fvars{t_0} \to \values, \sigma \uplus \nu_0 \vdash \fguard{t_0}} \implies \\
+	\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t}
+\end{multline*}
+\end{definition}
+As in the previous section, the definition can be simplified into a less intuitive version:
+\begin{definition}[Non-locking composition, working definition]
+\(A = A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is a non-locking composition if:
+\[ \forall s = \mpar{s_0, s'} \in S, V \uplus \biguplus_\subbox{t_0 \in \fOT{s_0}} \fvars{t_0} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_0 \in \fOT{s_0}} \fguard{t_0} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
+\end{definition}
+\begin{lem} The intuitive and working definition of non-locking composition are equivalent. \end{lem}
+We want to prove
+\[ \forall s = \mpar{s_p, s_c} \in S, V \uplus \biguplus_\subbox{t_p \in \fOT{s_p}} \fvars{t_p} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \tag{WD}\label{eq:nlcWD} \]
+\[ \bigsymb{\iff} \]
+\begin{multline*}
+	\forall s = \mpar{s_p, s_c} \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A}\mpar{s}} \implies \\
+	\mpar{\exists t_p \in \fOT{s_p}, \exists \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \vdash \fguard{t_p}} \implies \\
+	\mpar{\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t}} \tag{ID}\label{eq:nlcID}
+\end{multline*}
 

### 2021-07-26 2021-Refinement/paper/refinementarticle.tex
a bit more on deadlocks

@@
 
-Unfortunately, in the general case, this property is conflicting with the properties about the relation on automata because every property involving composition would be applicable on composition introducing deadlocks.
+Unfortunately, in the general case, this property is not much useful in general because it conflicts with the possibility to compose automata: The composition operator can itself introduce a deadlock.
+A way to solve the conflict between deadlock reduction and the properties involving composition is to only consider a composition that do not introduce deadlocks.
 
-\subsection{Issue with deadlock reduction and composition}
-A way to solve the conflict between deadlock reduction and the properties involving composition is to only consider a composition that do not introduce deadlocks.
-With this new condition on validity of composition we are able to define in the next sections a refinement relation where most of the properties of interest are satisfied.
-
-Before characterising a composition which does not introduce deadlocks we need to be able to tell which states are reachable because some deadlocks are not reachable and should not be considered as being introduced.
+Before characterising a composition which does not introduce deadlocks we need to be able to tell which states are reachable.
 \begin{definition}[Reachability]
-For any open automata \(A = \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is a predicate on states satisfying both
-
- Inital state is reachable: \(\sigma_0 \vdash \reach{A}\mpar{s_0}\)
-
- Reachability is preserved across transitions: \nmm{\forall t = \OTg \in T, \fvars{t} \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}}
+For any open automata \(A = \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is any predicate on states that is preserved accross transitions, and valdi on initial state:
+\[\sigma_0 \vdash \reach{A}\mpar{s_0}\quad\land\quad\forall t = \OTg \in T, \fvars{t} \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}\]
 \end{definition}
-The reachability predicate is used to characterise the reachable configurations in a run of an automaton.
-In fact the role of the predicate is to characterise potentially reachable configurations without having to characterise configurations as the result of a valid path in an automaton.
-
-To do that we impose that the initial configuration is reachable and that reachability is preserved by taking valid transitions.
-This effectively makes reachability take into account all paths, and potentially over-approximate the reachable configurations.
-The exact reachability may not be representable in the formulas, hence the need of potentially over-approximating.
+Reachability takes into account all paths, and potentially over-approximate the reachable configurations and must be representable as a formula.
+% LUDO HERE
 \begin{definition}[Non-locking composition, intuitive definition]

### 2021-07-26 2021-Refinement/paper/refinementarticle.tex
finally: V1 or deadlock preservation

@@
 \subsection{Open Automata}\label{sec:def}
- Open automata are labelled transition systems with variables  that can be used to compose other automata: they are made of transitions that are dependent of the actions of ``holes'', a composition operation consists in filling a hole with another automaton to obtain a more complete automaton.
-The variables makes the automata symbolic, and the holes allow for a partial definition of the behaviour.
+ Open automata (abbreviated OA) are labelled transition systems with variables  that can be used to compose other automata: they are made of transitions that are dependent of the actions of ``holes'', a composition operation consists in filling a hole with another automaton to obtain a more complete automaton.
+The variables makes the OA symbolic, and the holes allow for a partial definition of the behaviour.
 
-\begin{definition}[Open transition, Open automaton]
+\begin{definition}[Open transition, Open automaton (OA)]
 An \emph{open automaton} is a tuple \(\OAg\) with \(S\) the set of states, \(s_0 \in S\) the initial state, \(V\) the finite set of variable names, \(\sigma_0: V' \to \values\) the initial valuation of variables where \(V' \subseteq V\), \(J\) the set of hole names and \(T\) the set of open transitions.
@@
 \begin{definition}[Composition of open automata]
-The composition of \(A_c = \OAg[c]\) in the hole \(k \in J_p\) of \(A_p = \OAg[p]\) is the open automaton defined as follows.
+The composition of \(A_c = \OAg[c]\) in the hole \(k \in J_p\) of \(A_p = \OAg[p]\) is the OA defined as follows.
 \[
@@
 \end{definition}
-The first automaton decides when the second can evolve by involving its hole in a transition:
+The first OA decides when the second can evolve by involving its hole in a transition:
 The action emitted when \(A_c\) makes a transition is synchronised with the action of the hole \(k\) in transitions of \(A_p\) .
@@
 
-Similarly to FH-bisimulation we are interested here in finding relations between states of to open automata that contain variables and holes.
-However here we want to biuld a refinement relation that is a simulation but also guarantees that no deadlock is introduced.
+Similarly to FH-bisimulation~\cite{fhbisim} we are interested here in finding relations between states of to open automata that contain variables and holes.
+However here we want to build a refinement relation that is a simulation but also guarantees that no deadlock is introduced.
 Our objective is to characterize when a relation between two states of two open automata have the desired property.
@@
 
+\subsection{Deadlock Preservation, Reachability, and Composition}
+
 \begin{definition}[Deadlock reduction]\label{def:dpwd}
-A relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if  it satisfies the following:
-\[ \forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \]
+Let \(\OAg[1]\), \(\OAg[2]\) be two OAs.
+A relation on OA configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if  it satisfies the following:
+\begin{multline*}
+ \forall \mpar{s_1, s_2} \in S_1 \times S_2,\\ V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
+\end{multline*}
 \end{definition}
+
+\TODO{explain in particular why guards do the trick}
 
@@
 \begin{definition}[Reachability]
-For any open automata \(A = \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is any predicate on states that is preserved accross transitions, and valdi on initial state:
-\[\sigma_0 \vdash \reach{A}\mpar{s_0}\quad\land\quad\forall t = \OTg \in T, \fvars{t} \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}\]
+For any open automata \(A = \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is any predicate on states that is preserved across transitions, and valdi on initial state:
+\[\sigma_0 \vdash \reach{A}\mpar{s_0}\quad\land\quad\forall t = \OTg \in T, \fvars{t} \vdash \left(\reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}\right)\]
 \end{definition}
@@
 % LUDO HERE
-\begin{definition}[Non-locking composition, intuitive definition]
+\begin{definition}[Non-locking composition]
 Let \(A_i = \OAg[i], 0 \leq i \leq n\).
-The composition \(A = A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is non-locking if \(A\) has a reachability predicate satisfying:
-From reachable configurations, if there was a possible transition in \(A_0\) then there is a possible transition in \(A\).
-Formally for \(\OAg = A\), it gives
-\begin{multline*}
-	\forall s = \mpar{s'_i}_{0 \leq i \leq n} \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A}\mpar{s}} \implies \\
-	\mpar{\exists t_0 \in \fOT{s'_0}, \exists \nu_0: \fvars{t_0} \to \values, \sigma \uplus \nu_0 \vdash \fguard{t_0}} \implies \\
-	\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t}
-\end{multline*}
+The composition \(A = A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) 
+ is a non-locking composition if if \(A \) has a reachability predicate satisfying the following.
+From reachable configurations, if there was a possible transition in \(A_0\) then there is a possible transition in \(A\):
+\[ \forall s = \mpar{s_0, s'} \in S, V \uplus \biguplus_\subbox{t_0 \in \fOT{s_0}} \fvars{t_0} \vdash \left(\reach{A}\mpar{s} \wedge \bigvee_\subbox{t_0 \in \fOT{s_0}} \fguard{t_0} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \right)\]
 \end{definition}
-As in the previous section, the definition can be simplified into a less intuitive version:
-\begin{definition}[Non-locking composition, working definition]
-\(A = A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is a non-locking composition if:
-\[ \forall s = \mpar{s_0, s'} \in S, V \uplus \biguplus_\subbox{t_0 \in \fOT{s_0}} \fvars{t_0} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_0 \in \fOT{s_0}} \fguard{t_0} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
-\end{definition}
-\begin{lem} The intuitive and working definition of non-locking composition are equivalent. \end{lem}
-We want to prove
-\[ \forall s = \mpar{s_p, s_c} \in S, V \uplus \biguplus_\subbox{t_p \in \fOT{s_p}} \fvars{t_p} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \tag{WD}\label{eq:nlcWD} \]
-\[ \bigsymb{\iff} \]
-\begin{multline*}
-	\forall s = \mpar{s_p, s_c} \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A}\mpar{s}} \implies \\
-	\mpar{\exists t_p \in \fOT{s_p}, \exists \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \vdash \fguard{t_p}} \implies \\
-	\mpar{\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t}} \tag{ID}\label{eq:nlcID}
-\end{multline*}
+Again we use guards as a characteristics that the transition occurs.
 
-Hole - = relation
+\subsection{Refinement Relations for automata with the same holes}
+\TODO{Hole - = relation}
 

### 2021-07-26 2021-Refinement/paper/refinementarticle.tex
related work

--- 2021-07-26 2021-Refinement/paper/refinementarticle.tex
@@
 
-\usepackage{amsmath,amssymb,mathabx}
+\usepackage{amsmath,amssymb}
 %\usepackage{amsthm}
@@
 It is usually defined as trace inclusion or simulation \cite{Milner:1980}; this ensures that all behaviours of the implementation must be also behaviours of the specification.
-This definition, which is based on systems whose behaviour is fully defined, is not well-suited for open systems  as it requires to reason also about unspecified behaviours.
+This definition, which is based on systems whose behaviour is fully defined, is not well-suited for open systems,  as it requires to reason also about unspecified behaviours.
 
-There are some works that have been interested in the  the refinement of open systems.
-
-The definition of refinement for open systems in terms of alternating simulation \cite{Alur:1998} and \cite{deAlfaro:2021} is originating  from the game theory \cite{deAlfaro:2003}.
+There are some works that have focused on  the refinement of open systems. Defining refinement of open systems as trace inclusion  is  addressed  as a notion of subtyping in type theory 
+\cite{GayH:2005,BravettiZ:2021}.
+Such refinement is  instead based  on interface-oriented approach, it allows the expression more internal choices and less external choices.
+The refinement of open automata is defined in terms of  alternating simulation \cite{Alur:1998,deAlfaro:2021}, which is based on a process-oriented approach.
+Alternating simulation that is originating from the game theory \cite{deAlfaro:2003} allows  the study of relation between individual components by viewing them as alternating transition systems.
+In particular,  a refinement
+of automata expresses that the refined component can offer more services (input actions) and fewer service demands (output actions).
+The result of the composition of automata may
+contain illegal states, where one automaton issues an output that is not acceptable as input in the other one.
+An optimistic approach to compute compatibility between automata based on the fact that each automaton expects the other to provide  legal inputs, i.e, they can be composed together.
+Although our approach to design refinement differs from that of the above mentioned \cite{deAlfaro:2021},  because it is based on the notion of simulation, it has some commonalities:  our formalism is based on transition systems and on  optimistic approach to composition.
 
@@
  \(\fvars{e}\) is the set of variables in \(e \in E\) that are not bound by any binder. An expression is closed if \(\fvars{e}=\emptyset\).
-The set \(\values\) denote values which is a subset of closed terms. \(\rformulas[V]\) is the set of formulas $f$ that only use variables in $V$, i.e. the formulas such that  \(\fvars{f}\subseteq V\).
+The set \(\values\) denote values which is a subset of closed terms.
 
@@
 
-Similarly to FH-bisimulation we are interested here in finding relations between states of to open automata that contain variables and holes.
-However here we want to biuld a refinement relation that is a simulation but also guarantees that no deadlock is introduced.
-Our objective is to characterize when a relation between two states of two open automata have the desired property.
-Such a relation has the following signature: \( S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
-We first define when a relations is deadlock reducing, before characterising a first simple refinement relation only valid to compare automata with identical holes.
-
-\begin{definition}[Deadlock reduction]\label{def:dpwd}
-A relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if  it satisfies the following:
-\[ \forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \]
-\end{definition}
-
-Unfortunately, in the general case, this property is not much useful in general because it conflicts with the possibility to compose automata: The composition operator can itself introduce a deadlock.
-A way to solve the conflict between deadlock reduction and the properties involving composition is to only consider a composition that do not introduce deadlocks.
-
-Before characterising a composition which does not introduce deadlocks we need to be able to tell which states are reachable.
-\begin{definition}[Reachability]
-For any open automata \(A = \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is any predicate on states that is preserved accross transitions, and valdi on initial state:
-\[\sigma_0 \vdash \reach{A}\mpar{s_0}\quad\land\quad\forall t = \OTg \in T, \fvars{t} \vdash \reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}\]
-\end{definition}
-Reachability takes into account all paths, and potentially over-approximate the reachable configurations and must be representable as a formula.
-% LUDO HERE
-\begin{definition}[Non-locking composition, intuitive definition]
-Let \(A_i = \OAg[i], 0 \leq i \leq n\).
-The composition \(A = A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is non-locking if \(A\) has a reachability predicate satisfying:
-From reachable configurations, if there was a possible transition in \(A_0\) then there is a possible transition in \(A\).
-Formally for \(\OAg = A\), it gives
-\begin{multline*}
-	\forall s = \mpar{s'_i}_{0 \leq i \leq n} \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A}\mpar{s}} \implies \\
-	\mpar{\exists t_0 \in \fOT{s'_0}, \exists \nu_0: \fvars{t_0} \to \values, \sigma \uplus \nu_0 \vdash \fguard{t_0}} \implies \\
-	\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t}
-\end{multline*}
-\end{definition}
-As in the previous section, the definition can be simplified into a less intuitive version:
-\begin{definition}[Non-locking composition, working definition]
-\(A = A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is a non-locking composition if:
-\[ \forall s = \mpar{s_0, s'} \in S, V \uplus \biguplus_\subbox{t_0 \in \fOT{s_0}} \fvars{t_0} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_0 \in \fOT{s_0}} \fguard{t_0} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \]
-\end{definition}
-\begin{lem} The intuitive and working definition of non-locking composition are equivalent. \end{lem}
-We want to prove
-\[ \forall s = \mpar{s_p, s_c} \in S, V \uplus \biguplus_\subbox{t_p \in \fOT{s_p}} \fvars{t_p} \vdash \reach{A}\mpar{s} \wedge \bigvee_\subbox{t_p \in \fOT{s_p}} \fguard{t_p} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \tag{WD}\label{eq:nlcWD} \]
-\[ \bigsymb{\iff} \]
-\begin{multline*}
-	\forall s = \mpar{s_p, s_c} \in S, \forall \sigma: V \to \values, \mpar{\sigma \vdash \reach{A}\mpar{s}} \implies \\
-	\mpar{\exists t_p \in \fOT{s_p}, \exists \nu: \fvars{t_p} \to \values, \sigma \uplus \nu \vdash \fguard{t_p}} \implies \\
-	\mpar{\exists t \in \fOT{s}, \exists \nu: \fvars{t} \to \values, \sigma \uplus \nu \vdash \fguard{t}} \tag{ID}\label{eq:nlcID}
-\end{multline*}
+deadlock and reachability
 

### 2021-07-26 2021-Refinement/paper/refinementarticle.tex
completion de Related Work

@@
 The notion of refinement aims of capturing the relation between  a specification and an implementation of the same component.
-It is usually defined as trace inclusion or simulation \cite{Milner:1980}; this ensures that all behaviours of the implementation must be also behaviours of the specification.
+It is usually defined as trace inclusion or simulation \cite{Milner:1980, Kouchnarenko:2007}; this ensures that all behaviours of the implementation must be also behaviours of the specification.
 This definition, which is based on systems whose behaviour is fully defined, is not well-suited for open systems,  as it requires to reason also about unspecified behaviours.
@@
 Such refinement is  instead based  on interface-oriented approach, it allows the expression more internal choices and less external choices.
-The refinement of open automata is defined in terms of  alternating simulation \cite{Alur:1998,deAlfaro:2021}, which is based on a process-oriented approach.
+The refinement of open systems is also defined in terms of  alternating simulation \cite{Alur:1998,deAlfaro:2021}, which deals with game-based models.
 Alternating simulation that is originating from the game theory \cite{deAlfaro:2003} allows  the study of relation between individual components by viewing them as alternating transition systems.
-In particular,  a refinement
-of automata expresses that the refined component can offer more services (input actions) and fewer service demands (output actions).
-The result of the composition of automata may
-contain illegal states, where one automaton issues an output that is not acceptable as input in the other one.
-An optimistic approach to compute compatibility between automata based on the fact that each automaton expects the other to provide  legal inputs, i.e, they can be composed together.
-Although our approach to design refinement differs from that of the above mentioned \cite{deAlfaro:2021},  because it is based on the notion of simulation, it has some commonalities:  our formalism is based on transition systems and on  optimistic approach to composition.
+In particular,  a refinement of game-based automata expresses that the refined component can offer more services (input actions) and fewer service demands (output actions).
+However, the composition of such automata may
+lead to illegal states, where one automaton issues an output that is not acceptable as input in the other one.
+The theory of alternating simulation provides an optimistic approach to compute compatibility between automata based on the fact that each automaton expects the other to provide  legal inputs, i.e, two components can be composed if there is an environment where they can work together.
+As we shall see in this paper,
+our approach to design refinement  has some commonalities with that of the above mentioned \cite{deAlfaro:2021}: both are process-oriented approach even if they are not based on the same notion of simulation and they are based on optimistic approach to composition.
+For the composability, we shall see that we use the notion of comparability of holes (similar to the notion of compatibility), which is explicitly encompassed in the definition of composition.
 
@@
 
-Some related work on other models than open automata introduce refinement relations.
+\TODO{Some related work on other models than open automata introduce refinement relations.
 In a chapter by Bellegarde, Julliand and Kouchnarenko \cite{10.1007/3-540-46428-X_19}, a simulation relation on transition systems is introduced.
@@
 In our work we also deal with deadlocks but not with livelocks since the latter arise only with silent actions.
-This work is closer than the previous one to what we do here, still open automata are more expressive than LTS and composition is more general than sychronised composition.
+This work is closer than the previous one to what we do here, still open automata are more expressive than LTS and composition is more general than sychronised composition.}
 

### 2021-07-27 2021-Refinement/paper/refinementarticle.tex
reunion

@@
 
-\subsection{Deadlock Preservation, Reachability, and Composition}
+\subsection{Deadlock Reduction, Reachability, and Composition}
 
@@
 \begin{definition}[Reachability]
-For any open automata \(A = \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is any predicate on states that is preserved across transitions, and valdi on initial state:
+For any open automata \(A = \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is any predicate on states that is preserved across transitions, and valid on initial state:
 \[\sigma_0 \vdash \reach{A}\mpar{s_0}\quad\land\quad\forall t = \OTg \in T, \fvars{t} \vdash \left(\reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}\right)\]
@@
 \TODO{Hole - = relation}
+
+\TODO{pour rabea}
 

### 2021-07-28 2021-Refinement/paper/refinementarticle.tex
part

@@
 Also their composition is slightly different than the one on open automata because they can cause loops by linking two channels of the same process, where in open automata the composition makes an oriented tree.
-In their model there is an explicit deadlock and a succesful termination where in open automata there are no explicit termination.
+In their model there is an explicit deadlock and a successful termination where in open automata there are no explicit termination.
 We define a deadlock as a configuration without possible transition and assume what is a deadlock when comparing the open automata.
-To define their refinement and inheritance relation they use trace and failure semantics, which are weaker than (bi)simulations \cite{10.5555/640428.640430} and could break with open automata compositon.
+To define their refinement and inheritance relation they use trace and failure semantics, which are weaker than (bi)simulations \cite{10.5555/640428.640430} and could break with open automata composition.
 
@@
 
-\begin{definition}[Deadlock reduction]\label{def:dpwd}
-Let \(\OAg[1]\), \(\OAg[2]\) be two OAs.
+\begin{definition}[Deadlock reduction]\label{def:dpwd}\\
+Let \(\OAg[1]\) and \(\OAg[2]\) be two OAs.
 A relation on OA configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if  it satisfies the following:
@@
 \subsection{Refinement Relations for automata with the same holes}
-\TODO{Hole - = relation}
+\TODO{Hole - = relation pour rabea }
 
-\TODO{pour rabea}
+We generalise simulation between labelled transition systems to Hole-equal simulation  between  open automata that have exactly the same holes.
+\begin{definition}[Hole-equal simulation]
+Consider two OAs \(\OAg[1]\) and \(\OAg[2]\) with  \(J_1 = J_2\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $S_1$ to $S_2$ if the following conditions hold:
+\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
+\item[(2)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)\vspace{-8pt}
+\noindent\begin{multline*}
+	\mpar{\everymath{\displaystyle}\begin{array}{l}
+		\bigsymb{\forall} t_1 = \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
+		\quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
+		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
+			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}}
+	\end{array}} \\
+	\wedge \mpar{V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
+\end{multline*}
+\end{definition}
+Note in this definition, instead of matching an instantiated transition of the first automata to another instantiated transition of the second, it matches an open transition $t_1$ to a family of covering open transitions $t_{2x}^{x\in X}$.
+Note also the second part of the conjunction of condition 2 expresses the deadlock reduction between automata.
+
+Intuitively, this means that for every pair of related
+states $(s_1,s_2)$  of the two automata, and for every each transition of the first automaton from $s_1$, there is a matching transitions  of the second automaton  from $s_2$ such that the produced action match, the actions of the same holes and the successors are related after variable update.
 

### 2021-07-29 2021-Refinement/paper/refinementarticle.tex
relecture hole - = simu

@@
 
-We generalise simulation between labelled transition systems to Hole-equal simulation  between  open automata that have exactly the same holes.
+We define here simulation between labelled transition systems to Hole-equal simulation  between  open automata that have exactly the same holes.
 \begin{definition}[Hole-equal simulation]
@@
 		\bigsymb{\forall} t_1 = \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
-		\quad \mpar{\forall x \in X, J'_{2x} \cap J_1 = J'_1 \cap J_2} \\[-10pt]
-		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+		\quad \mpar{\forall x \in X, J'_{2x}= J'_1} \\[-10pt]
+		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash \left( R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
 			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
 			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}}
+		\end{array}}\right)
 	\end{array}} \\
@@
 Intuitively, this means that for every pair of related
-states $(s_1,s_2)$  of the two automata, and for every each transition of the first automaton from $s_1$, there is a matching transitions  of the second automaton  from $s_2$ such that the produced action match, the actions of the same holes and the successors are related after variable update.
+states $(s_1,s_2)$  of the two automata, and for every  transition of the first automaton from $s_1$, there is a set of matching transitions  of the second automaton  from $s_2$ such that the produced action match, the actions of the same holes and the successors are related after variable update.
 

### 2021-07-29 2021-Refinement/paper/refinementarticle.tex
comment section 4.2

@@
 Note in this definition, instead of matching an instantiated transition of the first automata to another instantiated transition of the second, it matches an open transition $t_1$ to a family of covering open transitions $t_{2x}^{x\in X}$.
-Note also the second part of the conjunction of condition 2 expresses the deadlock reduction between automata.
+Note also the second part of the conjunction of condition (2) expresses the deadlock reduction between automata (as introduced in Definition \ref{def:dpwd}).
 
@@
 states $(s_1,s_2)$  of the two automata, and for every  transition of the first automaton from $s_1$, there is a set of matching transitions  of the second automaton  from $s_2$ such that the produced action match, the actions of the same holes and the successors are related after variable update.
+Our definition captures a simple kind of sub-classing of open automata with the same holes.
+It is stronger than a strict simulation since it matches a transition with a family of transitions.
+With such a relation we are able to check the refinement between two open automata corresponding to the same component but specified differently, for example, by duplicating states, removing transitions,  reinforcing  guards, modifying variables, etc...
+
+%Technically,  it expresses how the concepts from the abstract and the refined systems are linked together.
 

### 2021-07-29 2021-Refinement/paper/refinementarticle.tex
General refinement V0

--- 2021-07-29 2021-Refinement/paper/refinementarticle.tex
@@
 		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash \left( R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x}} \beta_{1j} = \beta_{2xj} \\[12pt]
 			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
@@
 
+Above we designed a refinement relation that compares OAs with the same holes, it ensures simulation at the automaton level, with symbolic evaluation of the guards and transitions.
+We want now to extend this to automata where the set of holes is not the same.
+A trivial usecase for this is filling a hole with a completely defined automaton.
+In this case, we want to ensure that the automaton with a filled hole is a refinement of the other automata: actions of the identical holes will be taken into account the same way, and filling the hole partially reduces the behaviour of the automaton.
+
+The major challenge in this case is to maintain a form of transitivity while being able to take into account the actions of some of the holes.
+A naive definition of refinement would ensure that the holes that are identical in the two OAs are taken into account in the simulation.
+Unfortunately this does not work well with transitivity as if $A_1$ simulates $A_2$ and $A_2$ simulates $A_3$, and one hole appears in $A_3$ and in $A_1$ but not in $A_2$ then we have no proven property on the way $A_1$ and $A_3$ takes his hole into account, and in general  $A_1$ does not simulate $A_3$.
+The way we solve this issue is to remember in the simulation relation which holes have been compared.
+This way the relation is parameterized by the set of holes that belong to the two automata and are taken into account.
+In practice, when performing successive refinements, we  keep track of which holes are in common at each step of refinement.
+\begin{definition}[Open automata refinement]
+For two open automata \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a refinement of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), is defined as:
+\begin{multline*}
+	\exists R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2], \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge \forall \mpar{s_1, s_2} \in S_1 \times S_2, \\
+	\mpar{\everymath{\displaystyle}\begin{array}{l}
+		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\[12pt]
+		\quad \mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H} \\[-10pt]
+		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \\
+			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}} \\
+	\end{array}} \\
+	\wedge V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
+\end{multline*}
+Giving \(R\) and \(H\) is sufficient to characterise the refinement, so we call \(\mpar{R, H}\) a hole-tracking simulation of \(A_1\) by \(A_2\).
+Hole in \(H\) are called tracked holes.
+\end{definition}
+It is important to note that every action of the holes outside \(H\) is unconstrained in the related automata.
+It is easy to see that the hole-equal simulation is a particular case of openautomata refinement, specialized on the case where $J_1=J_2=H$.
+
 \section{Properties}\label{sec:prop}

### 2021-07-30 2021-Refinement/paper/refinementarticle.tex
minor
A word on guards

@@
 
-\TODO{explain in particular why guards do the trick}
+One important aspect to notice is that in this definition, because of the symbolic nature of pNets and their structure, the fact that a guard is true is sufficient to reason on the possible paths.
+This slightly simplifies the definition and makes the characterisation of transition that can be triggered more symbolic.
+An equivalent  definition of deadlock reduction can be expressed: it states that if there is a transition that can be triggered in the first automaton, then there is a transition from the related state in the second automaton that can be triggered.
+This second definition is more complex, in particular because of the multiple quantifiers over transitions and automaton state.
 
@@
 It is important to note that every action of the holes outside \(H\) is unconstrained in the related automata.
-It is easy to see that the hole-equal simulation is a particular case of openautomata refinement, specialized on the case where $J_1=J_2=H$.
+It is easy to see that the hole-equal simulation is a particular case of openautomata refinement, when  $J_1=J_2=H$.
 

### 2021-07-30 2021-Refinement/paper/refinementarticle.tex
petit ajout

--- 2021-07-29 2021-Refinement/paper/refinementarticle.tex
@@
 It is stronger than a strict simulation since it matches a transition with a family of transitions.
-With such a relation we are able to check the refinement between two open automata corresponding to the same component but specified differently, for example, by duplicating states, removing transitions,  reinforcing  guards, modifying variables, etc...
+With such a relation we are able to check the refinement between two open automata corresponding to the same component but specified differently, for example, by duplicating states, removing transitions,  reinforcing  guards, modifying variables.
+However, this refinement is inappropriate is the setting of composability which is the main advantage of the pNets-based approach.
+Refinement through composition  leads to a model, in which composition can be used both to add new holes to a system and to restrict the holes already present to a subset.
 

### 2021-07-30 2021-Refinement/paper/refinementarticle.tex
prospectie proprietes?

--- 2021-07-30 2021-Refinement/paper/refinementarticle.tex
@@
 \subsection{Refinement Relations for automata with the same holes}
-\TODO{Hole - = relation pour rabea }
 
@@
 It is important to note that every action of the holes outside \(H\) is unconstrained in the related automata.
-It is easy to see that the hole-equal simulation is a particular case of openautomata refinement, when  $J_1=J_2=H$.
+It is easy to see that the hole-equal simulation is a particular case of open automata refinement, when  $J_1=J_2=H$.
 
@@
 \TODO{1.5 pages}
+
+- reflexivity and transitivity
+
+- composition is a refinement (under which condition?)
+
+- what is the property wrt deadlocks?
+
+- congruence? a[b/j] if $a'$ refines $a$ and if $b'$ refines $b$?
+
+- relation with fh bisimulation
 

### 2021-07-30 2021-Refinement/paper/refinementarticle.tex

@@
 %
-\title{Refinements for open pNets}
+\title{Refinements for open automata}
 %
@@
 
-One important aspect to notice is that in this definition, because of the symbolic nature of pNets and their structure, the fact that a guard is true is sufficient to reason on the possible paths.
+One important aspect to notice is that in this definition, because of the symbolic nature of OAs and their structure, the fact that a guard is true is sufficient to reason on the possible paths.
 This slightly simplifies the definition and makes the characterisation of transition that can be triggered more symbolic.
@@
 \noindent\begin{multline*}
-\mpar{\everymath{\displaystyle}\begin{array}{l}
+\everymath{\displaystyle}\begin{array}{l}
 		\bigsymb{\forall} t_1 = \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
-		\quad \mpar{\forall x \in X, J'_{2x}= J'_1} \\[-10pt]
+		\quad \mpar{\forall x \in X, J'_{2x}= J'_1} \\[-2pt]
 		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash \left( R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
@@
 		\end{array}}\right)
-	\end{array}} \\
-	\wedge \mpar{V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
+	\end{array} 
+%\\
+%	\wedge \mpar{V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
 \end{multline*}
+\item[(3)] $R$ is deadlock reducing.
 \end{definition}
@@
 It is stronger than a strict simulation since it matches a transition with a family of transitions.
-With such a relation we are able to check the refinement between two open automata corresponding to the same component but specified differently, for example, by duplicating states, removing transitions,  reinforcing  guards, modifying variables, etc...
+With such a relation we are able to check the refinement between two open automata with the same level of abstraction but specified differently, for example, by duplicating states, removing transitions,  reinforcing  guards, modifying variables.
+However, this refinement is inappropriate in the setting of composition which is the main advantage of the open automaton-based approach. 
+\TODO{introduce somewhere refinement through composition} 
+Refinement through composition  leads to a model in which composition can be used both to add new holes to a system and to fill holes, obtaining a system with less holes.
+Next section will identify a refinement relation with the possibility to have different holes in the compared automata.
 
@@
 \begin{definition}[Open automata refinement]
-For two open automata \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a refinement of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), is defined as:
+For two open automata \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a refinement of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a deadlock reducing relation $R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that:
+ \[\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}}\]
+and
 \begin{multline*}
-	\exists R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2], \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge \forall \mpar{s_1, s_2} \in S_1 \times S_2, \\
-	\mpar{\everymath{\displaystyle}\begin{array}{l}
+ \forall \mpar{s_1, s_2} \in S_1 \times S_2, \\
+	\everymath{\displaystyle}\begin{array}{l}
 		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\[12pt]
-		\quad \mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H} \\[-10pt]
-		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+		\quad \mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H} \\[-1pt]
+		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash \mpar{R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
 			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \\
 			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}} \\
-	\end{array}} \\
-	\wedge V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
+		\end{array}}} \\
+	\end{array} \\
 \end{multline*}
+
 Giving \(R\) and \(H\) is sufficient to characterise the refinement, so we call \(\mpar{R, H}\) a hole-tracking simulation of \(A_1\) by \(A_2\).

### 2021-07-30 2021-Refinement/paper/refinementarticle.tex
comment def 8

@@
 \nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} is not agreed because it would produce a transition whose guard is not satisfiable.
-It will produce the following transition: \nmm{\OT{R2C}{R3C}{\tau}{\mbrc{}}{\top \wedge \top \wedge c < t \wedge \act{set}\mpar{x} = \act{tick} \wedge \theta\mpar{x} = \delta\mpar{x}}{\mbrc{c \gets c + 1}}}.
+It will produce the following transition: \nmm{\OT{R2C}{R3C}{\tau}{\mbrc{}}{\top \wedge \top \wedge c < t \wedge \act{set}\mpar{x} = \act{tick} \wedge \theta\mpar{x} = \delta\mpar{x}}{\mbrc{c \gets c + 1}}} which requires to be triggered  the equality of completely different actions.
 
@@
 Note in this definition, instead of matching an instantiated transition of the first automata to another instantiated transition of the second, it matches an open transition $t_1$ to a family of covering open transitions $t_{2x}^{x\in X}$.
-Note also the second part of the conjunction of condition (2) expresses the deadlock reduction between automata (as introduced in Definition \ref{def:dpwd}).
+%Note also the second part of the conjunction of condition (2) expresses the deadlock reduction between automata (as introduced in Definition \ref{def:dpwd}).
 
@@
 We want now to extend this to automata where the set of holes is not the same.
-A trivial usecase for this is filling a hole with a completely defined automaton.
+A trivial use-case for this is filling a hole with a completely defined automaton.
 In this case, we want to ensure that the automaton with a filled hole is a refinement of the other automata: actions of the identical holes will be taken into account the same way, and filling the hole partially reduces the behaviour of the automaton.

### 2021-07-30 2021-Refinement/paper/refinementarticle.tex
just drafting the contributions

--- 2021-07-30 2021-Refinement/paper/refinementarticle.tex
@@
 \TODO{1.5 pages}
+
+Contributions:
+
+We first: introduce open automata (NOT NEW), their composition, and the deadlock-free composition.
+
+Then we define a refinement relation for open automata that has the following characteristics:
+
+- good behaviour wrt composition
+
+- refinement does not introduce deadlock
+
+- a first relation that focuses on the automaton part and a second that deals partially with open behaviour
+
+we will see that having at the same time composition and transitivity also raises challenges; we introduce a relation that addresses this challenge.
 

### 2021-08-05 2021-Refinement/paper/refinementarticle.tex
Example

@@
 In our work we also deal with deadlocks but not with livelocks since the latter arise only with silent actions.
-This work is closer than the previous one to what we do here, still open automata are more expressive than LTS and composition is more general than sychronised composition.}
+This work is closer than the previous one to what we do here, still open automata are more expressive than LTS and composition is more general than synchronised composition.}
 
@@
 \centering
+\input{Traffic_Lights_Interm.tex}
+\caption{The incomplete Specification Traffic Lights system}
+\label{fig:tlf}
+\end{figure}
+
+\begin{figure}
+\centering
 \input{Traffic_Lights_Full.tex}

### 2021-08-09 2021-Refinement/paper/refinementarticle.tex
def reprise

@@
 \begin{definition}[Composition of open automata]
-The composition of \(A_c = \OAg[c]\) in the hole \(k \in J_p\) of \(A_p = \OAg[p]\) is the OA defined as follows.
-\[
-	A_p\subst{A_c}{k} ::=  \OA{S_p \times S_c}{\mpar{s_{0p}, s_{0c}}}{V_p \uplus V_c}{\sigma_{0p} \uplus \sigma_{0c}}{J_c \uplus J_p \setminus \mbrc{k}}{T} \]
+The composition of \(A_c = \OAg[c]\) in the hole \(k \in J_p\) of \(A_p = \OAg[p]\) is the OA defined as follows:
+\[A_p\subst{A_c}{k} ::=  \OA{S_p \times S_c}{\mpar{s_{0p}, s_{0c}}}{V_p \uplus V_c}{\sigma_{0p} \uplus \sigma_{0c}}{J_c \uplus J_p \setminus \mbrc{k}}{T} \] \text{with }
 
 \begin{align*}
-	\text{with } T = & \mset{\OT{\mpar{s_p, s_c}}{\mpar{s'_p, s'_c}}{\alpha_p}{\beta_j^{j \in J'_c \uplus J'_p}}{g_p \wedge g_c \wedge \alpha_c = \beta_k}{\psi_p \uplus \psi_c}}{ \OT{s_p}{s'_p}{\alpha_p}{\beta_j^{j \in J'_p \uplus \mbrc{k} }}{g_p}{\psi_p} \in T_p, \OTx{c}{}{}{c} \in T_c} \\
+T=& \mset{\OT{\mpar{s_p, s_c}}{\mpar{s'_p, s'_c}}{\alpha_p}{\beta_j^{j \in J'_c \uplus J'_p}}{g_p \wedge g_c \wedge \alpha_c = \beta_k}{\psi_p \uplus \psi_c}}{ \OT{s_p}{s'_p}{\alpha_p}{\beta_j^{j \in J'_p \uplus \mbrc{k} }}{g_p}{\psi_p} \in T_p, \OTx{c}{}{}{c} \in T_c} \\
 	& \cup \mset{\OT{\mpar{s_p, s_c}}{\mpar{s'_p, s_c}}{\alpha_p}{\beta_j^{j \in J'_p}}{g_p}{\psi_p}}{\OTx{p}{}{}{p} \in T_p, k \notin J'_p, s_c \in S_c}
@@
 \end{definition}
+
 Note in this definition, instead of matching an instantiated transition of the first automata to another instantiated transition of the second, it matches an open transition $t_1$ to a family of covering open transitions $t_{2x}^{x\in X}$.
@@
 Refinement through composition  leads to a model in which composition can be used both to add new holes to a system and to fill holes, obtaining a system with less holes.
-Next section will identify a refinement relation with the possibility to have different holes in the compared automata.
+Next section will identify a refinement relation with the possibility to have different holes in the compared automata.\\
+
+\TODO{Je ne suis pas sure que la def precedente soit correcte: il faut ajouter la notion de  configuration comme suit:}
+
+\begin{definition}[Hole-equal simulation]
+Consider two OAs \(\OAg[1]\) and \(\OAg[2]\) with  \(J_1 = J_2\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $S_1$ to $S_2$ if the following conditions hold:
+\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
+\item[(2)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)\vspace{-8pt}
+\noindent\begin{multline*}
+\everymath{\displaystyle}\begin{array}{l}
+		\bigsymb{\forall} t_1 = \OTx{1}{}{1}{1} \in \fOT{s_1},  \forall \sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values,\\
+\bigsymb{\exists} \mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}\!\!\!\!, 
+	\exists \sigma':\biguplus_\subbox{t_{2x} \in \fOT{s_2}} \fvars{t_{2x}}   \to \values\\
+		   \mpar{\forall x \in X, J'_{2x}= J'_1} \\[-2pt]
+%		\nwedge  
+		\left( \sigma  \vdash  R\mpar{s_1, s_2} \wedge g_1 \implies \sigma \uplus \sigma' \vdash \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x}} \beta_{1j} = \beta_{2xj} \nwedge \\[12pt]
+			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}}\right)
+	\end{array} 
+%\\
+%	\wedge \mpar{V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
+\end{multline*}
+\item[(3)] $R$ is deadlock reducing.
+\end{definition}
 
@@
 
+It  is  easy  to  show  that  the  refinement  is  reflexive  and  transitive,  so  it  is  a  preorder on the set of open automata.
+
 - composition is a refinement (under which condition?)

### 2021-08-10 2021-Refinement/paper/refinementarticle.tex
reflexivite

@@
 
-It  is  easy  to  show  that  the  refinement  is  reflexive  and  transitive,  so  it  is  a  preorder on the set of open automata.
+We will  show  that  the  refinement  is  reflexive  and  transitive,  so  it  is  a  preorder on the set of open automata.
+
+\begin{lemma} The relation \(\wrel{}{}{H}\) is a preorder thus enables stepwise refinement.
+\end{lemma}
+The relation  \(\wrel{}{}{H}\) is reflexive,  \(\wrel{A}{A}{H}\),  by taking $\mpar{R\mpar{s_1, s_2}} \mapsto $ to be $s_1= s_2$ and  and checking the above conditions, we can see that\\
 

### 2021-08-12 2021-Refinement/paper/refinementarticle.tex
typos

@@
 In practice, when performing successive refinements, we  keep track of which holes are in common at each step of refinement.
-\begin{definition}[Open automata refinement]
+\begin{definition}[Open automata refinement]\label{Def:OA-Refinement}
 For two open automata \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a refinement of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a deadlock reducing relation $R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that:
@@
 \end{lemma}
-The relation  \(\wrel{}{}{H}\) is reflexive,  \(\wrel{A}{A}{H}\),  by taking $\mpar{R\mpar{s_1, s_2}} \mapsto $ to be $s_1= s_2$ and  and checking the above conditions, we can see that\\
+The relation  \(\wrel{}{}{H}\) is reflexive,  \(\wrel{A}{A}{H}\),  by taking $R\mpar{s_1, s_2} \mapsto \displaystyle\bigwedge_\subbox{v \in vars(s_1)} {v=v}$ to be $s_1= s_2$  and checking the above conditions (Definition \ref{Def:OA-Refinement}), we can see that\\
 

### 2021-08-17 2021-Refinement/report.tex
Fixed issues with partial valuations by removing the partial part

@@
 \begin{defi}[Open automaton]
-An open automaton is a tuple \(\OAg\) with \(S\) the set of states, \(s_0 \in S\) the initial state, \(V\) the set of variable names unique to this automaton, \(\sigma_0: V' \to \values\) the initial valuation of variables where \(V' \subseteq V\), \(J\) the set of hole names and \(T\) the set of open transitions.
+An open automaton is a tuple \(\OAg\) with \(S\) the set of states, \(s_0 \in S\) the initial state, \(V\) the set of variable names unique to this automaton, \(\sigma_0: V \to \values\) the initial valuation of variables, \(J\) the set of hole names and \(T\) the set of open transitions.
 A pair of a state and a valuation is called a configuration.
@@
 
-The initial valuation is a partial valuation of the variables.
-If an undefined variable is set before being read, it behaves like an initially set variable.
-If an undefined variable is not set before being read then its value may be any fixed value.
-When we will introduce refinements in Section \ref{sec:prelref}, setting an undefined variable will be considered a valid refinement, for instance a \(5\) bits register is a particular \(n\) bits register.
+The initial valuation is a valuation of the automaton variables.
+We could have defined it as a partial valuation in order to allow some variable to be parameters of the automaton and to allow not defining some variables never read before being set.
+However the first is unnecessary because it is already possible by having a variable set once in the first transition by an unbound and unconstrained variable in a transition as we will see after the next definition.
+And for the second point we could also define such a variable to any value.
 \begin{defi}[Open transition, Instanciated transition]
@@
 The LTS is partial in the sense that one can plug an LTS in the hole and the surrounding LTS will react to the actions emitted by the sub-LTS put in the hole.
-Initially the automaton is in the initial state with an extension on all the variables of the initial valuation.
+Initially the automaton is in the initial state with the initial valuation.
 In any configuration, it can perform instanciated transitions which source state is the current state and which guard is satisfiable in the current valuation if the holes emit the indicated actions.
@@
 By performing the instanciated transition, the automaton emits the indicated action and updates its configuration according to the target state and variable assignments.
+To illustrate how a variable can be used as a parameter we could imagine how to represent a \(n\)-bit buffer: \(n \in V\) is initially set to any value in the initial valuation, then the first transition, taken only once, could have guard \(\top\) (always true) and variable assignement \(\mbrc{n \gets k}\) with \(k \notin V\) an unbound variable.
 \begin{noti}[FH-bisimulation]
@@
 The open transitions do not indicate the source and target states since that is the role of the transitions arrows; only the emitted action is on the bottom side of open transitions.
-Initial valuations are indicated near a double lined arrow pointing to the initial state.
+Relevant initial variable values are indicated near a double lined arrow pointing to the initial state.
 \begin{figure}
@@
 This property is useful if we want to characterise the kind of operations that can generate any refined automaton starting from the specification.
-We won't have it because extending the definition domain of the initial valuation will be a refinement which can't be expressed with composition.
+We won't have it because some operation impossible with composition, like merging states, can applied to open automata and give FH-bisimilar ones and FH-bisimulation compatibility is a much more important property.
 Yet a ``completeness w.r.t.\@ some set of operations" is still a strong and interesting property.
@@
 \begin{itemize}
-\item In the state \(0S\) any valuation is reachable (no initial valuation).
+\item In the state \(0S\), the initial valuation and valuations with \(0 \leq c = t\) are reachable for both automata.
+	On top of that, every valuations where \(c \geq t\) are reachable in the right automaton.
 	In both automata the transition \nmm{\OT{0S}{1S}{\tau}{\mbrc{}}{\top}{\mbrc{}}} has a true guard, hence the first branch of the disjunction holds.
@@
 The hole-equal simulation is applicable when the related automata have the same holes.
-It is designed to capture all the refinements other than composition: Duplicating and merging states and transitions, changing variables, removing transitions, adding requirements to guards, specifying more initial variables, and many more.
+It is designed to capture all the refinements other than composition: Duplicating and merging states and transitions, changing variables, removing transitions, adding requirements to guards, and many more.
 

### 2021-08-18 2016-Weak-FH-Bisim/WeakBisim.tex
first comments

@@
 An indexed family is denoted as
-follows: $a_i^{i\in I}$ is a family of elements $a_i$ indexed over the
+follows: $t_i^{i\in I}$ is a family of elements $t_i$ indexed over the
 set $I$. Such a family
-is equivalent to the mapping $(i\mapsto a_i)^{i\in I}$, and we will also use mapping 
+is equivalent to the mapping $(i\mapsto t_i)^{i\in I}$, and we will also use mapping 
 notations to manipulate indexed sets.
@@
 
-Consequently, $a_i^{i\in I}$ defines first $I$ the set over which the
+Consequently, $t_i^{i\in I}$ defines first $I$ the set over which the
 family is indexed, and then $a_i$ the elements of the family.
-For example $a^{i\in\{3\}}$ is
-the mapping with a single entry $a$ at index $3$; exceptionally, such mappings with
-only a few entries will also be denoted $(3\mapsto a)$.
+For example $t^{i\in\{3\}}$ is
+the mapping with a single entry $t$ at index $3$; exceptionally, for mappings with
+only a few entries we use the notation $(3\mapsto t)$ instead.
 %The operation  $A[j \mapsto a]$ updates the value associated to $j$ in map $A$ so that 
@@
 %An empty family is denoted $[]$. % (it can be defined as $a_i^{i\in\emptyset}$).
-To simplify equations, an indexed set can be denoted $\set{a}$
-instead of $a_i^{i\in I}$ when $I$ is irrelevant.
+To simplify equations, an indexed set can be denoted $\set{t}$
+instead of $t_i^{i\in I}$ when $I$ is irrelevant.
 
@@
 	\end{mathpar}
-	Where $J'\subseteq J$, $s, s'\in\mathcal{S}$ and $\beta_j$
+	Where $J'\subseteq J$ is the set of holes involved in the transition; $s, s'\in\mathcal{S}$ are states of the automaton; and $\beta_j$
         is a transition of the hole $j$, with $\beta_j\in\Sort_j$. $\alpha$ is an action 
@@
  On the other side, open transition rules (with dotted lines) are logical implications, but using a simple logic (this logic includes the boolean expressions $\AlgB$, boolean operators, and term equality).
-   open transitions could typically be handled in a 
- mechanised way.
+%  Open transitions could typically be handled in a 
+% mechanised way.
 
@@
 allows us to refine the predicate, or substitute any free variable by
-an expression. More formally, let $\Pred$ be any predicate and $\Post$ any substitution such that $V\cap \dom(\Post)=\emptyset$. Then we have the following
-implication:
-
+an expression. More formally:
+
+For all predicate $\Pred$, for all substitution $\Post$ such that $V\cap \dom(\Post)=\emptyset$. We have: 
 		 \begin{mathpar}

### 2021-08-19 2016-Weak-FH-Bisim/WeakBisim.tex
Working on comments

@@
 %\overfullrule=1mm
+\usepackage[multiple]{footmisc}
 \usepackage[T1]{fontenc}
@@
 
-pNets is a generalisation of automata that includes parameters, and hierarchical composition.
+pNets is a generalisation of automata that includes variables and hierarchical composition.
 Open pNets are pNets with holes, i.e.
@@
 
-We distinguish two kinds of parameterised actions: one that distinguishes input variables and one that does not. 
+We define two kinds of parameterised actions. The first kind distinguishes input variables and the second kind does not. 
 We first define the set of actions that distinguish input variables, they will be used in the definition of \pLTS\ below:
@@
 $\symb{?}$.
-We additionally suppose that each input variable does not
+We additionally impose that each input variable does not
 appear somewhere else in the same action term:
@@
 $a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs), but it also allows
-for more general synchronisation mechanisms, like gate negociation in Lotos, or broadcast
+for more general synchronisation mechanisms, like gate negotiation in Lotos, or broadcast
 communications.
@@
 
-When this is not ambiguous, we shall use abusive vocabulary and
+When this is not ambiguous, we shall use abusive notations and
 notations for sets, and typically write ``indexed set over I'' when  
@@
 
-$\uplus$ is the disjoint union on sets. We extend it to  disjoint union  of indexed 
+The disjoint union on sets is $\uplus$. We extend it to  disjoint union  of indexed 
 sets defined by the merge of the 
@@
 
-We denote $y\gets e$ a substitution. The application of the substitution is denoted
+We denote $y\gets e$ a substitution~. The application of the substitution is denoted
 $\subst{y\gets e}$, the operation replaces in a term all occurrences 
@@
 
-For this property to be valid even if the substitution does not operate on all variables,
+For this property to be valid when the substitution does not operate on all variables,
 we define the composition operation as follows: 
@@
 \begin{array}{l}
-\Sortop(\mylangle S,s_0,V, \to\myrangle) = \{\alpha\subst{?x \gets x| 
-x\in\symb{iv}(\alpha)}|s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
+\Sortop(\mylangle S,s_0,V, \to\myrangle) = \{\Sortop(\alpha)|s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
     J}\rangle} s'\in \to \} \\
@@
 \set{\symb{SV}\,}\myrangle)
-=\{\alpha' |\, \SV{\set{\alpha}}{\alpha'}{e_b}\in\set{\symb{SV}}\,\}
+=\{\Sortop(\alpha') |\, \SV{\set{\alpha}}{\alpha'}{e_b}\in\set{\symb{SV}}\,\}\\
+\Sortop(\alpha(p_1,..,p_n))=(\alpha,n)
 \end{array}
@@
 \item
-The set of holes $\Holes(\pNet)$ of a pNet is the indexes of the holes of the pNet 
+The set of holes $\Holes(\pNet)$ of a pNet is the indices of the holes of the pNet 
 itself plus the indexes of all the holes of its sub-pNets.
@@
 \end{array}\]
+
 \item
@@
 is said to be \emph{open}.
+Sort come naturally with a compatibility relation that is similar tp a type-compatibility check.
+We simply say that two sorts are compatible ifthey consist of the same actions with the same arity.
+In practice, it is sufficient to check the equality of the two sets of pairs $(\alpha,n)$ of the two sorts.
 \end{definition}
@@
 Synchronisation between sub-pNets is defined by synchronisation vectors that express how an action of a sub-pNet can be synchronised with actions of other sub-pNet, and how the resulting synchronised action is visible to the outside of the pNet.
+Consider for example a pNet that assembles several pLTSs, the synchronisation vectors express transitions of the composing pNet: each vector expresses not only the actions emitted by the pNet but also what transitions of the composed pLTSs must occur to trigger this global transition.
 Synchronisation vectors can also express the exportation of an action of a sub-pNet to the next level, or to hide an interaction and make it non-observable.
@@
 	\set{\symb{SV}}\,\myrangle$
- can be (partially) filled by providing  a pNet $\pNetQ$ of the
-	right sort to fill one of  its holes.	
-	Suppose $j_0\in J$:
+ can be (partially) filled by providing  a pNet $\pNetQ$ to fill one of  its holes.	
+	Suppose $j_0\in J$ and $\Sortop(\pNetQ)$ and $\Sort_{j_0}$ are compatible:
 	%% \[\mylangle \pNet_i^{i\in I},S_j^{j\in J}, \symb{SV}_k^{k\in
@@
 	Where $J'\subseteq J$ is the set of holes involved in the transition; $s, s'\in\mathcal{S}$ are states of the automaton; and $\beta_j$
-        is a transition of the hole $j$, with $\beta_j\in\Sort_j$. $\alpha$ is an action 
+        is a transition of the hole $j$, with $\Sortop(\beta_j)\in\Sort_j$. $\alpha$ is an action 
         label denoting the resulting action of this open transition.
@@
 %        $\beta_j$ and $\alpha$, and the state variables of $s$.
-        \Pred\ is a predicate over the  variables in $V$ and all variables
-        in the different terms
-       $\beta_j$ and $\alpha$. \Post\ is a set of 
-	assignments that are effective after the open transition, they are
+        \Pred\ is a predicate over the  variables in $V\cup\vars(\alpha)\cup
+			{\displaystyle \bigcup_{j\in J'}\vars(beta_j)}$. \Post\ is a set of 
+	assignments (i.e., indexed substitutions) that are effective after the open transition, they are
         represented as a substitution of the form $({x_k\gets e_k})^{k\in K}$ 
 	where $\forall k.\, x_k\in V$, and $e_k$ are expressions
-        over the variables $V$ and all variables
-        in the different terms
-       $\beta_j$ and $\alpha$. The assignments are always applied simultaneously because the variables in $V$ can be in both sides. Open transitions are identified
+        over the variables variables in $V\cup\vars(\alpha)\cup
+			{\displaystyle \bigcup_{j\in J'}\vars(beta_j)}$. The assignments are always applied simultaneously because the variables in $V$ can be in both sides. Open transitions are identified
         modulo logical equivalence on their predicate. 
@@
 inference rule. They correspond to two different logical levels.
-On one side, classical (black) inference rules  use  an expressive logic and are paper rules.
- On the other side, open transition rules (with dotted lines) are logical implications, but using a simple logic (this logic includes the boolean expressions $\AlgB$, boolean operators, and term equality).
+On one side, classical (black) inference rules  use  an expressive logic (like any other computer science article).
+ On the other side, open transition rules (with dotted lines) are logical implications, but using a  logic with a specific syntax and that can be mechanized (this logic includes the boolean expressions $\AlgB$, boolean operators, and term equality).
 %  Open transitions could typically be handled in a 
@@
 
-We take in this article a semantics and logical understanding of these
-automata. Open automata are closed by a simple form of refinement that
+While the definition and usage of the open transition can be formalised and taken in a pure syntactic acceptation, we take in this article a semantics and logical understanding of open automata. 
+Formally, open automata are closed by a simple form of refinement that
 allows us to refine the predicate, or substitute any free variable by
-an expression. More formally:
+an expression as expressed below.
 
@@
 
-Another consequence of the semantics and logical interpretation of the
+Another aspect of the logical interpretation of the
 formulas is that we make no distinction between the equality and the
 equivalence on boolean formulas, i.e. equivalence of two predicates
-$\Pred$ and $\Pred\,'$ can be denoted $\Pred=\Pred\,'$.
+$\Pred$ and $\Pred\,'$ can be denoted $\Pred=\Pred\,'$. $=$ is not interpreted in a syntactical way.
 
@@
 We define now a bisimulation relation adapted to open automata and their parametric nature.
-The relation relates states of the open automaton and states equivalence between the open transitions between the states.
-Its key characteristics are 1) the introduction of predicates in the bisimulation relation: as states may contain variables, relation between states may depend on the value of the variables; 2) the bisimulation property relates elements of the open transitions and take into account predicates over variables, actions of the holes, and state modifications.
+This relation relates states of the open automaton and states equivalence between the open transitions between the states.
+Its key characteristics are 1) the introduction of predicates in the bisimulation relation: as states may contain variables, relation between states may depend on the value of the variables; 2) the bisimulation property relates elements of the open transitions and takes into account predicates over variables, actions of the holes, and state modifications.
  We name it FH-bisimulation,
@@
 A relation over the states of two open automata  $\mylangle J,\mathcal{S}_1, s_0,V_1,
-   \mathcal{T}_1 \myrangle$ and $\mylangle !J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2 \myrangle$ has the form $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$, it relates states of $\mathcal{S}_1$ and 
+   \mathcal{T}_1 \myrangle$ and $\mylangle J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2 \myrangle$ has the form $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$, it relates states of $\mathcal{S}_1$ and 
 $\mathcal{S}_2$ constrained by a predicate.
@@
       if $\Pred_{s,t}$       is 
-      True, i.e. the states are related when the variables in $V_1$ and $V_2$ verify the 
-      predicate $\Pred_{s,t}$. By nature, this is well-defined if the variables of the two open automata are disjoint, i.e.  $V_1\cap V_2=\emptyset$.
+      True, i.e.
+the states are related when the value of the variables in $s$ and $t$  verify the predicate $\Pred_{s,t}$.
+Note that this implies that the free variables of  $\Pred_{s,t}$ belong to $V_1$ and $V_2$.
+Each variable used in $\Pred_{s,t}$ should refer to a state variable of $s$ or $t$ and there must be no ambiguity on the referenced variable.
+Consequently, the considered relation is well-defined if the variables of the two open automata are disjoint, i.e.
+$V_1\cap V_2=\emptyset$.
  FH-bisimulation is defined formally: 
@@
 	\Holes(\pNet)$, $I_2=M\cap \Leaves(\pNet)$,  $I_1=M\setminus J \setminus 
-	I_2$}.                                                                    
+	I_2$}\footnote{It is of course possible to replace $I_1$ and $I_2$ by their formal definition but the rule would be more difficult to read.}.
 \begin{mathpar}
@@
 It somehow implies that the theory of open pNets is convenient to study properties of process composition.
-Open pNets can indeed be used to study process operators and process algebras, as shown in~\cite{henrio:Forte2016}, or to study interaction protocols~\cite{BHHM:FACS11}.
+Open pNets can indeed be used to study process operators and process algebras, as shown in~\cite{henrio:Forte2016} where compositional properties are extremely useful.
+In the case of interaction protocols~\cite{BHHM:FACS11}, composition of bisimulation can justify abstractions used in some parts of the application.
 
@@
 cannot change its internal state because a hole did a $\tau$ transition.
-The second statement ensures that there cannot be in the open automaton other transitions that would be able to observe a $\tau$ action from a hole.
+The second statement ensures that there cannot be in the open automaton other transitions that would be able to observe a $\tau$ action from a hole: statement (2) states that all the open transitions where a hole does  a $\tau$ must be of the shape given in statement (1).
 The condition $J=\{j\}$ is a bit restrictive, it could safely be replaced by $\forall j\in J.\, \beta_j=\tau$, allowing the other holes to perform $\tau$ transitions too (because these $\tau$ actions cannot be observed).
@@
 This property justifies the fact that we can abstract away $\tau$ transitions from holes in the definition of a weak open transition.
+We define weak open transitions similarly to open transitions except that holes can perform \emph{sequences of observable actions} instead of single actions (observable or not).
 
@@
 $s\in\mathcal{S}_1$ and
-$t\in\mathcal{S}_2$ such that $(s,t|\Pred)\in\mathcal{R}$, we 
+$t\in\mathcal{S}_2$ such that $(s,t|\Pred_{s,t})\in\mathcal{R}$, we 
    have the following:
@@
  and  \\
- $\Pred \land \Pred_{OT}\\
+ $\Pred_{s,t} \land \Pred_{OT}\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!

### 2021-08-19 2016-Weak-FH-Bisim/WeakBisim.tex
More comments

@@
 only a few entries we use the notation $(3\mapsto t)$ instead.
+Note that, sentences of the form ``there exists $t_i^{i\in I}$'' means there exists $I$ and a function that maps each element of $I$ to a term $t_i$.
 %The operation  $A[j \mapsto a]$ updates the value associated to $j$ in map $A$ so that 
@@
 \end{mathpar}
- there exist   open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
+ there exist an indexed set of  open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
  \begin{mathpar}
@@
 If we assume that everything is finite (states and transitions in the
-open automata, and the predicates in $\mathcal{R}$), then it is easy to
+open automata), then it is easy to
 prove that it is decidable whether a relation is a 
@@
 and $\mathcal{R}$ a relation over their states $\mathcal{S}_1$ and
-$\mathcal{S}_2$ constrained by a finite set of predicates. Assume that
+$\mathcal{S}_2$ constrained by a set of predicates. Assume that
 the predicates inclusion is decidable over  
@@
 
-The definition of bisimulation for open automata allows us to derive a
-bisimulation theory for open pNets. As pNets are composition
+The definition of bisimulation for open automata allows us to derive the characterisation and properties of a
+bisimulation relation for open pNets. As pNets are composition
 structures, it then makes sense to prove composition lemmas: we prove
@@
 	with the resulting action of the vector. The sub-pNets involved are split between two 
-	sets, $I_2$ for sub-pNets that are pLTSs, and $I_1$ for the others, $J$ is the set of 
+	sets, $I_2$ for sub-pNets that are pLTSs (with open transitions obtained by rule \textbf{Tr1}), and $I_1$ for the sub-pNets that are not pLTSs (with open transitions obtained by rule \textbf{Tr2}), $J$ is the set of
 	holes involved in the transition\footnote{Formally, if $SV_k \!=\! \SV{({\alpha'})_m^{m 
@@
 	\Holes(\pNet)$, $I_2=M\cap \Leaves(\pNet)$,  $I_1=M\setminus J \setminus 
-	I_2$}\footnote{It is of course possible to replace $I_1$ and $I_2$ by their formal definition but the rule would be more difficult to read.}.
+	I_2$}\footnote{It is of course possible to replace $I_1$ and $I_2$ by their formal definition in \textbf{Tr2} but the rule would be more difficult to read.}.
 \begin{mathpar}

### 2021-08-20 2016-Weak-FH-Bisim/WeakBisim.tex
Two easy comments
Meeting

@@
 \begin{itemize}
-\item[$\bullet$] $\pNet_i^{i\in I}$ is the family of sub-pNets indexed over $I$. $vars(P_i)$ and $vars(P_j)$ must be disjoint for $i\neq j$.
+\item[$\bullet$] $I$ is a set of indices and $\pNet_i^{i\in I}$ is the family of sub-pNets indexed over $I$. $vars(P_i)$ and $vars(P_j)$ must be disjoint for $i\neq j$.
 %  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which sub-pNets are indexed.
@@
 We define weak open transitions similarly to open transitions except that holes can perform \emph{sequences of observable actions} instead of single actions (observable or not).
+Compared to the definition of open transition, this small change has the significant impact as a single weak transition is the composition of several transitions of the holes.
 
@@
 
-This article defines a strong and a weak bisimulation principles that are adapted to parameterised systems and hierarchical composition.
+This article defines a strong and a weak bisimulation relation that are adapted to parameterised systems and hierarchical composition.
 Our bisimulation principle handles pNet parameters in the sense that two states might be or not in relation depending on the value of parameters.

### 2021-08-24 2016-Weak-FH-Bisim/WeakBisim.tex
make V2
missing last change in makefile + addressed issues on relation and sets of OT in the fh bisim

@@
 
+Bisimulation over a symbolic and open model like open pNets or open automata is  different from the classical notion of bisimulation because it cannot rely on the equality over a finite set of action labels.
+Classical bisimulations require to exhibit, for each transition of one system, a transition of the other system that simulates it.
+Instead, bisimulation for open automata  rely on the simulation of each open transition of one automaton by a set of open transitions of the other one, that should cover all the
+cases where the original transition can be triggered.
+
 \subsubsection*{Structure}
@@
 This is very convenient to model systems and encode futures or message routing.
+
 pNets have been used to model GCM distributed component systems, illustrating the expressiveness of the model~\cite{AmeurBoulifa2017}.
@@
 The theory of pNets as operators able to fully take into account open systems is given in the following sections.
+Comparing formally the existing direct operational semantics and the semantics derived from open automata in the current article would be an interesting partial proof of soundness for our semantics.
+The proof could only be partial as the formal semantics that exist only consider closed and fuully instantiated pNets.
+Proving a bisimulation between the semantics presented in this article and the operational one shown in~\cite{AmeurBoulifa2017} is outside the scope of this article.
 
@@
 
-A relation over the states of two open automata  $\mylangle J,\mathcal{S}_1, s_0,V_1,
-   \mathcal{T}_1 \myrangle$ and $\mylangle J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2 \myrangle$ has the form $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$, it relates states of $\mathcal{S}_1$ and 
-$\mathcal{S}_2$ constrained by a predicate.
-More precisely, for any pair $(s,t)\in \mathcal{S}_1\times \mathcal{S}_2$, there is a 
+One of the original aspects of FH-bisimulation is due to the symbolic nature of open automata.
+Indeed, a single state of the automaton represents a potentially infinite number of concrete states, depending on the value of state variables, and a single open transition of the automaton may also be instantiated with an unbounded number of value for the transition parameters.
+Consequently it would be too restrictive to impose that each transition of one automaton is matched by exactly one transition of the bisimilar automaton.
+Thus the definition of bisimulation requires that, for each open transition of one automaton, there exists a matching  set of open transitions covering the original one, indeed depending on the value of action parameters or state variables different open transitions might simulate the original one provided the reached states are bisimilar.
+
+The second original aspect is the nature of the bisimulation relation.
+ A classical relation between states can be seen as a function mapping pairs of state to a boolean value (true if the states are related, false if they are not).
+A FH-bisimulation relation maps pairs of states to boolean expressions that use variables of the two states.
+Each variable used in $\Pred_{s,t}$ should refer to a state variable of $s$ or $t$ and there must be no ambiguity on the referenced variable, we thus require that the two compared automata have disjoint state variables.
+Formally, a relation over the states of two open automata  $\mylangle J,\mathcal{S}_1, s_0,V_1,
+   \mathcal{T}_1 \myrangle$ and $\mylangle J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2 \myrangle$ has the signature $\mathcal{S}_1\times\mathcal{S}_2\to\AlgB$. 
+We adopt a notation similar to standard relations and denote it
+ $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$. 
+The relation $\mathcal{R}$ must verify the following constraints: 1) For any pair $(s,t)\in \mathcal{S}_1\times \mathcal{S}_2$, there is a 
    single
@@
 the states are related when the value of the variables in $s$ and $t$  verify the predicate $\Pred_{s,t}$.
-Note that this implies that the free variables of  $\Pred_{s,t}$ belong to $V_1$ and $V_2$.
-Each variable used in $\Pred_{s,t}$ should refer to a state variable of $s$ or $t$ and there must be no ambiguity on the referenced variable.
-Consequently, the considered relation is well-defined if the variables of the two open automata are disjoint, i.e.
+2) The free variables of  $\Pred_{s,t}$ belong to $V_1$ and $V_2$, i.e.
+$\vars(\Pred_{s,t})\subseteq V_1\cup V_2$, and the variables of the two open automata are disjoint, i.e.
 $V_1\cap V_2=\emptyset$.
@@
 \begin{minipage}{0.30\linewidth}
-	\includegraphics[width=\linewidth]{XFIG/Bisim.pdf}
+	\includegraphics[width=\linewidth]{XFIG/Bisim}
 \end{minipage}

### 2021-08-26 2016-Weak-FH-Bisim/WeakBisim.tex
comparison with previous works on pnets

@@
 While most of our previous works relied on closed, fully-instantiated semantics~\cite{BBCHM:article2008,AmeurBoulifa2017,HKM-FASE16}, it is only recently that we could design a first version of a  parameterised semantics for pNets with a strong bisimulation equivalence~\cite{henrio:Forte2016}.
-This article builds upon this previous parameterised semantics and provides a cleaner version of the semantics with a slightly simplified formalism.
+This article builds upon this previous parameterised semantics and provides a clean and complete version of the semantics with a slightly simplified formalism that makes proofs easier.
 It also adds a notion of global state to automata.
@@
 pNets have been used to model GCM distributed component systems, illustrating the expressiveness of the model~\cite{AmeurBoulifa2017}. 
-These works show that pNets are convenient to express the behaviour of the system in a compositional way, which is crucial for the definition of the semantics, especially when dealing with a hierarchical component system like GCM.
+These works show that pNets are convenient to express the behaviour of the system in a compositional way, which is crucial for the definition of the semantics, especially when dealing with a hierarchical component system.
 Unfortunately, the semantics of pNets and the existing tools at this point were only able to deal with a closed system completely instantiated: pNets could be used as composition operator in the definition of the semantics, which was sufficient to perform finite-state model checking on a closed system, but there was no theory for the use of pNets as operators and no tool for proving properties on open system.
-The semantics of closed pNets~\cite{AmeurBoulifa2017}, defined as an instantiation of labelled transition systems, is not necessary to understand this article but can be useful to  understand the semantics of pNets in a simpler and more operational setting.
+Consequently, much of the formalisation efforts did not use holes and the interplay between holes, sorts, and synchronisation vector was not formalised.
+In previous works~\cite{AmeurBoulifa2017}, only closed pNets were equipped with a semantics, it was defined as an instantiation of labelled transition systems.
+The old semantics is not necessary to understand this article but it defines the semantics of pNets in a simpler and more operational setting.
 The theory of pNets as operators able to fully take into account open systems is given in the following sections.

### 2021-08-27 2016-Weak-FH-Bisim/WeakBisim.tex
pnets vs oas

@@
 transitions~\cite{deSimone85,Larsen87}. 
+These works use the term \emph{parameter} to designate systems where variables defining the system as a strong influence on their behaviour: in parametrised systems, parameters can typically influence the number of processes in the system or the way they interact.
 In \cite{IngolfsdottirL:2001,HennessyLin:TCS95}, Lin, Ingolfsdottir and Hennessy developed a full hierarchy of
@@
 
+\subsubsection*{pNets and open automata}
+pNets is a convenient model to model concurrent systems in a hierarchical and parametrised way.
+The coordination between processes is expressed as synchronisation vectors that allows the definition of complex and expressive synchronisation patterns.
+open pNets are pNets for which one of the element in the hierarchy is still undefined, such undefined element is called \emph{hole}; a hole can be \emph{filled} later by providing another pNet.
+ The semantics of pNets can be expressed as a translation to a labelled transition system, but only if the pNet has no parameter or it has holes.
+Adding parameters to a LTS is quite standard but enabling holes inside LTSs is not a well-defined notion.
+We thus define \emph{open automata} that can be seen as LTSs with parameters and holes.
+The transitions of open automata are much more complex than transitions of an LTS as the firing on a transition depends on parameters and actions that are symbolic.
+This article defines the notion of \emph{open transition} a transition that is symbolic in terms of parameters and coordinated actions.
+
+Contrarily to pNets, open automata are not hierarchical structure, thus they are more convenient for formal reasoning but not adapted to the definition of a complex and structured system like pNets.
+Additionally, open transitions are expressed in terms of logics more than in terms of synchronised actions, synchronisation vectors on the contrary make it easy to express synchronisations that exist in process algebra or distributed systems.
+
+This article defines pNets and illustrate with an example how they can be used to provide the model of a communicating system.
+Then we introduce open automata to provide a semantics to open pNets and introduce bisimulation relations and their properties.
+Open automata can be also seen as an algebra that can be studied independently from its application to pNets but the composition properties make more sense in a hierarchical model like pNets.
+
 \subsubsection*{Previous Works and Contribution}
@@
 It also adds a notion of global state to automata.
-The slight simplification of the formalism allowed us to adopt a much cleaner presentation where the theory for open automata.
-The algebra used to define the semantics of pNets with holes, can be studied independently from its application to pNets.
 Also, in \cite{henrio:Forte2016} the study of compositionability was only partial, and in particular the proof that bisimulation is an equivalence is one new contribution of this article and provides a particularly interesting insight on the semantic model we use.

### 2021-08-30 2016-Weak-FH-Bisim/WeakBisim.tex
substitutions redefined

@@
 
-We denote $y\gets e$ a substitution~. The application of the substitution is denoted
-$\subst{y\gets e}$, the operation replaces in a term all occurrences 
-of the variable $y$ by the expression $e$. 
-$\Post$ ranges over (indexed) sets of substitutions; $\subst{\Post}$ is the substitution that applies all the substitutions defined by $\Post$ in a parallel manner.
-$\otimes$ is the composition operator on substitutions, such that for any term $t$ we have: $t\subst{\Post\shortotimes\Post'} = (t\subst{\Post'})\subst{\Post}$.
-
-For this property to be valid when the substitution does not operate on all variables,
-we define the composition operation as follows: 
+This article also uses substitutions.
+Applying a substitution inside a term $t$ is denoted $t\subst{y_i\gets e_i}^{i\in I}$ and consists in replacing in parallel all the occurrences of variables $y_i$ in the term $t$ by the terms $e_i$.
+Note that a substitution is defined by a partial function that is applied on the variables inside a term.
+We let $\Post$ range over partial functions that are used as substitution and use the notation $\{y_i\gets e_i\}^{i\in I}$ to define such a partial function\footnote{Note that the fact that substitutions are defined from partial function  implies that each $y_i$ is different.}.
+ $\subst{\Post}$ is thus the operation that applies,  in a parallel manner,  the substitution defined by the partial function $\Post$.
+$\otimes$ is a composition operator on these partial functions, such that for any term $t$ we have: $t\subst{\Post\shortotimes\Post'} = (t\subst{\Post'})\subst{\Post}$.
+This property must also be valid when the substitution does not operate on all variables.
+We thus define the composition operation as follows: 
 %\TODO{version d eric reprise et corrigee}

### 2021-08-30 2016-Weak-FH-Bisim/WeakBisim.tex
more on substitutions

@@
 We let $\Post$ range over partial functions that are used as substitution and use the notation $\{y_i\gets e_i\}^{i\in I}$ to define such a partial function\footnote{Note that the fact that substitutions are defined from partial function  implies that each $y_i$ is different.}.
+These partial functions are sometimes called \emph{substitution functions} in the following.
  $\subst{\Post}$ is thus the operation that applies,  in a parallel manner,  the substitution defined by the partial function $\Post$.
@@
 This property must also be valid when the substitution does not operate on all variables.
-We thus define the composition operation as follows: 
+We thus define a composition operation as follows: 
 %\TODO{version d eric reprise et corrigee}
@@
 			{\displaystyle \bigcup_{j\in J'}\vars(beta_j)}$. \Post\ is a set of 
-	assignments (i.e., indexed substitutions) that are effective after the open transition, they are
-        represented as a substitution of the form $({x_k\gets e_k})^{k\in K}$ 
+	assignments that are effective after the open transition, they are
+        represented as a substitution function: $({x_k\gets e_k})^{k\in K}$ 
 	where $\forall k.\, x_k\in V$, and $e_k$ are expressions
         over the variables variables in $V\cup\vars(\alpha)\cup
-			{\displaystyle \bigcup_{j\in J'}\vars(beta_j)}$. The assignments are always applied simultaneously because the variables in $V$ can be in both sides. Open transitions are identified
+			{\displaystyle \bigcup_{j\in J'}\vars(beta_j)}$.
+The assignments are always applied simultaneously because the variables in $V$ can be in both sides ($x_k$s are distinct).
+Open transitions are identified
         modulo logical equivalence on their predicate. 
@@
 
-For all predicate $\Pred$, for all substitution $\Post$ such that $V\cap \dom(\Post)=\emptyset$. We have: 
+For all predicate $\Pred$, for all partial functions $\Post$ such that $V\cap \dom(\Post)=\emptyset$. We have: 
 		 \begin{mathpar}
@@
 applies in parallel the  
-substitutions $\Post_{OT}$ and $\Post_{OT_x}$ (parallelism is crucial
+substitution defined by the partial functions $\Post_{OT}$ and $\Post_{OT_x}$ (parallelism is crucial
 inside each $\Post$ set but not between  $\Post_{OT}$ and
@@
 This rules carefully composes predicates, effects, and actions of the holes, indeed in the rule, predicate $\Pred_2$ manipulates variables of $s_1$ that result from the first weak open transition.
-Their values thus depend on the initial state but also on the effect (as a substitution $\Post_1$) of the first weak open transition.
-In the same manner, $\Pred_3$ must be applied the joint substitution $\Post_2\shortotimes\Post_1$.
+Their values thus depend on the initial state but also on the effect (as a substitution function $\Post_1$) of the first weak open transition.
+In the same manner, $\Pred_3$ must be applied the substitution defined by the composition $\Post_2\shortotimes\Post_1$.
 Similarly, effects on variables must be applied to obtain the global effect of the composed weak open transition, it must also be applied to observable actions of the holes, and to the global action of the weak open transition.
@@
 We concentrate on weak open transitions $WI_3$ and $WI_4$.
-Let us denote as $post_n$ the effect (substitution) of the strong open transitions $SI_n$ from Figure \ref{SimpleProtCounter:ImplOA}:
+Let us denote as $post_n$ the effect (as a substitution function) of the strong open transitions $SI_n$ from Figure \ref{SimpleProtCounter:ImplOA}:
 \smallskip
@@
 
-Then the effect of one single $100 \xrightarrow{OT_4} 210 \xrightarrow{OT_5} 220 \xrightarrow{OT_6} 100$ loop is\footnote{when showing  the result of $Posts$ composition, we will omit the identity substitutions introduced by the $\shortotimes$ definition in page \pageref{def:substitutions}}:
+Then the effect of one single $100 \xrightarrow{OT_4} 210 \xrightarrow{OT_5} 220 \xrightarrow{OT_6} 100$ loop is\footnote{when showing  the result of $Posts$ composition, we will omit the identity substitution functions introduced by the $\shortotimes$ definition in page \pageref{def:substitutions}}:
 \[post_{456} = post_6 \shortotimes\ post_5 \shortotimes\ post_4
@@
 
-By construction, four substitutions $\subst{~}$ only have an effect on the  
+By construction, four substitution functions $\subst{~}$ only have an effect on the  
 variables of the open automaton they belong to, they also produce terms containing only 
 variables of the open automaton they belong to. Finally, because of the domain of the 
-substitutions of the predicates, we have:\\
+substitution functions of the predicates, we have:\\
        	$\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\land 
@@
 \end{multline*}
-Note that  on the right side of the implication we added  the substitution  of $\Post_{OT_x}$ without affecting the validity of the statement, because  the domain  of the substitution $\Post_{OT_x}$ is disjoint from the others.
+Note that  on the right side of the implication we added  the substitution  of $\Post_{OT_x}$ without affecting the validity of the statement, because  the domain  of the substitution function $\Post_{OT_x}$ is disjoint from the others.
 Hence a little rewriting gives:
@@
 \vis{\beta_{2j}}\subst{\Post_1}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}\land \Pred_{OT_a}\land\\\Pred_{OT_{b}}\subst{\Post_{OT_a}} \land  \alpha'\subst{\Post_1}= \alpha_{2 b} \subst{\Post_{OT_a}} \land (\Pred_{s_{21},v_b} \land  \Pred_3)\\ \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{b}}\shortotimes\Post_{OT_a}})\end{multline*}
-Again note that because of the domain  of the substitution is independent from some predicates and expressions, we removed $\Post_1$ and  we  added the term $\Post_{OT_{b}}\shortotimes\,\Post_{OT_a}$ in the substitution of the right side of the implication.\\
+Again note that because of the domain  of the substitution function is independent from some predicates and expressions, we removed $\Post_1$ and  we  added the term $\Post_{OT_{b}}\shortotimes\,\Post_{OT_a}$ in the substitution of the right side of the implication.\\
 Finally, by replacing the predicate $(\Pred_{s_{21},b} \land  \Pred_3)$

### 2021-08-31 2016-Weak-FH-Bisim/2021-09-letter2Reviewers.tex
squelette de lettre de reponse

\documentclass{article}
\usepackage{a4wide}
\title{Reply to reviewers\\
LMCS \#\,6784 Manuscript: \\``Compositional equivalences based on Open pNets'' }

\begin{document}

\maketitle
\noindent
Dear Editor, dear reviewers,

Please find enclosed the revision of our submission to LMCS. We improved our article according to the comments made by the
anonymous reviewers.

We would first like to thank the reviewers for their analysis of our
paper, and the useful advices they gave us.

We detail below the major changes we made in this revision. After
this, we will review in the next pages the comments of the reviewers
and explain how we addressed them.  \emph{Comments that could be
  addressed trivially and exactly as suggested by the reviewers are
  omitted}.  \bigskip

In this new version, you will find the major improvements listed below:
\begin{itemize}
\item 
\end{itemize}

\bigskip
\noindent
Best regards,
\newline
\noindent
Rab\'ea Ameur-Boulifa, Ludovic Henrio, Eric Madelaine.

\newpage
As explained above, we quote below and reply to text requiring changes that we did not 
address in a straightforward manner. Major points of the reviews have not been omitted in 
any case.

\section*{Annex 1: response to first reviewers' comments}

\section*{Annex 2: response to second reviewers' comments}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2021-09-07 2016-Weak-FH-Bisim/WeakBisim.tex
Update WeakBisim.tex
Corrige des typos dans les premieres modifs de Ludo

@@
 Consequently, $t_i^{i\in I}$ defines first $I$ the set over which the
-family is indexed, and then $a_i$ the elements of the family.
+family is indexed, and then $t_i$ the elements of the family.
 For example $t^{i\in\{3\}}$ is
@@
 
-When this is not ambiguous, we shall use abusive notations and
-notations for sets, and typically write ``indexed set over I'' when  
+When this is not ambiguous, we shall use abusive notations 
+%and notations 
+for sets, and typically write ``indexed set over I'' when  
 formally we should speak of multisets, and ``$x\in
@@
 is said to be \emph{open}.
-Sort come naturally with a compatibility relation that is similar tp a type-compatibility check.
-We simply say that two sorts are compatible ifthey consist of the same actions with the same arity.
+Sort come naturally with a compatibility relation that is similar to a type-compatibility check.
+We simply say that two sorts are compatible if they consist of the same actions with the same arity.
 In practice, it is sufficient to check the equality of the two sets of pairs $(\alpha,n)$ of the two sorts.
@@
 Comparing formally the existing direct operational semantics and the semantics derived from open automata in the current article would be an interesting partial proof of soundness for our semantics.
-The proof could only be partial as the formal semantics that exist only consider closed and fuully instantiated pNets.
-Proving a bisimulation between the semantics presented in this article and the operational one shown in~\cite{AmeurBoulifa2017} is outside the scope of this article.
+The proof could only be partial as the formal semantics that exists only consider closed and fully instantiated pNets.
+Proving
+% a bisimulation
+an equivalence between the semantics presented in this article and the operational one shown in~\cite{AmeurBoulifa2017} is outside the scope of this article.
 
@@
 While the definition and usage of the open transition can be formalised and taken in a pure syntactic acceptation, we take in this article a semantics and logical understanding of open automata. 
-Formally, open automata are closed by a simple form of refinement that
+Formally, the open transition sets in open automata are closed by a simple form of refinement that
 allows us to refine the predicate, or substitute any free variable by
@@
 equivalence on boolean formulas, i.e. equivalence of two predicates
-$\Pred$ and $\Pred\,'$ can be denoted $\Pred=\Pred\,'$. $=$ is not interpreted in a syntactical way.
+$\Pred$ and $\Pred\,'$ can be denoted $\Pred=\Pred\,'$, where the $=$ symbol is not interpreted in a syntactical way.
 
@@
 One of the original aspects of FH-bisimulation is due to the symbolic nature of open automata.
-Indeed, a single state of the automaton represents a potentially infinite number of concrete states, depending on the value of state variables, and a single open transition of the automaton may also be instantiated with an unbounded number of value for the transition parameters.
+Indeed, a single state of the automaton represents a potentially infinite number of concrete states, depending on the value of state variables, and a single open transition of the automaton may also be instantiated with an unbounded number of values for the transition parameters.
 Consequently it would be too restrictive to impose that each transition of one automaton is matched by exactly one transition of the bisimilar automaton.
@@
 We define weak open transitions similarly to open transitions except that holes can perform \emph{sequences of observable actions} instead of single actions (observable or not).
-Compared to the definition of open transition, this small change has the significant impact as a single weak transition is the composition of several transitions of the holes.
+Compared to the definition of open transition, this small change has a significant impact as a single weak transition is the composition of several transitions of the holes.
 

### 2021-09-16 2016-Weak-FH-Bisim/WeakBisim.tex
Update WeakBisim.tex
Quelques typos pages 1 et 2

@@
 
-Establishing equivalences between programs or system is crucial both for verifying correctness of programs, by establishing that two implementations are equivalent, and for justifying optimisations and program transformations, by establishing that a modified program is equivalent to the source one.
+Establishing equivalences between programs or systems is crucial both for verifying correctness of programs, by establishing that two implementations are equivalent, and for justifying optimisations and program transformations, by establishing that a modified program is equivalent to the source one.
 There exist several equivalence relations for programs, and bisimulations are among the most versatile of these equivalences.
-Among bisimulation relations one distinguishes strong bisimulation, that requires that each action of a program is simulated by a single action of the equivalent program, a weak bisimulation that  is a coarser relations, allowing some of the actions to be
+Among bisimulation relations one distinguishes strong bisimulation, that requires that each action of a program is simulated by a single action of the equivalent program, a weak bisimulation that  is a coarser relation, allowing some of the actions to be
   invisible or internal moves, and thus not simulated by the equivalent program.
@@
 transitions~\cite{deSimone85,Larsen87}. 
-These works use the term \emph{parameter} to designate systems where variables defining the system as a strong influence on their behaviour: in parametrised systems, parameters can typically influence the number of processes in the system or the way they interact.
+These works use the term \emph{parameter} to designate systems where variables defining the system have a strong influence on their behaviour: in parametrised systems, parameters can typically influence the number of processes in the system or the way they interact.
 In \cite{IngolfsdottirL:2001,HennessyLin:TCS95}, Lin, Ingolfsdottir and Hennessy developed a full hierarchy of
@@
 pNets is a convenient model to model concurrent systems in a hierarchical and parametrised way.
-The coordination between processes is expressed as synchronisation vectors that allows the definition of complex and expressive synchronisation patterns.
-open pNets are pNets for which one of the element in the hierarchy is still undefined, such undefined element is called \emph{hole}; a hole can be \emph{filled} later by providing another pNet.
- The semantics of pNets can be expressed as a translation to a labelled transition system, but only if the pNet has no parameter or it has holes.
+The coordination between processes is expressed as synchronisation vectors that allow the definition of complex and expressive synchronisation patterns.
+Open pNets are pNets for which some elements in the hierarchy are still undefined, such undefined elements are called \emph{holes}; a hole can be \emph{filled} later by providing another pNet.
+ The semantics of pNets can be expressed as a translation to a labelled transition system, but only if the pNet has no parameter and no holes.
 Adding parameters to a LTS is quite standard but enabling holes inside LTSs is not a well-defined notion.
@@
 
-Contrarily to pNets, open automata are not hierarchical structure, thus they are more convenient for formal reasoning but not adapted to the definition of a complex and structured system like pNets.
-Additionally, open transitions are expressed in terms of logics more than in terms of synchronised actions, synchronisation vectors on the contrary make it easy to express synchronisations that exist in process algebra or distributed systems.
-
-This article defines pNets and illustrate with an example how they can be used to provide the model of a communicating system.
+Contrarily to pNets, open automata are not hierarchical structures, thus they are more convenient for formal reasoning but not adapted to the definition of a complex and structured system like pNets.
+Additionally, open transitions are expressed in terms of logics more than in terms of synchronised actions, synchronisation vectors on the contrary make it easy to express synchronisations that exist in process algebra orin specification and high-level languages for distributed systems.
+
+This article defines pNets and illustrates with an example how they can be used to provide the model of a communicating system.
 Then we introduce open automata to provide a semantics to open pNets and introduce bisimulation relations and their properties.
-Open automata can be also seen as an algebra that can be studied independently from its application to pNets but the composition properties make more sense in a hierarchical model like pNets.
+Open automata can be also seen as an algebra that can be studied independently from its application to pNets but their composition properties make more sense in a hierarchical model like pNets.
 

### 2021-09-21 2016-Weak-FH-Bisim/WeakBisim.tex
Update WeakBisim.tex
seance avec Rabea...: british, state vars, etc

@@
 \usepackage{lmodern}
-%\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
+%\usepackage{geometry}                % See geometry.pdf to learn the layout
 %\geometry{a4paper}                   % ... or a4paper or a5paper or ...
@@
 transitions~\cite{deSimone85,Larsen87}. 
-These works use the term \emph{parameter} to designate systems where variables defining the system have a strong influence on their behaviour: in parametrised systems, parameters can typically influence the number of processes in the system or the way they interact.
+These works use the term \emph{parameter} to designate systems where variables defining the system have a strong influence on their behaviour: in parameterised systems, parameters can typically influence the number of processes in the system or the way they interact.
 In \cite{IngolfsdottirL:2001,HennessyLin:TCS95}, Lin, Ingolfsdottir and Hennessy developed a full hierarchy of
@@
 \subsubsection*{pNets and open automata}
-pNets is a convenient model to model concurrent systems in a hierarchical and parametrised way.
+pNets is a convenient model to model concurrent systems in a hierarchical and parameterised way.
 The coordination between processes is expressed as synchronisation vectors that allow the definition of complex and expressive synchronisation patterns.
@@
 One of the original aspects of FH-bisimulation is due to the symbolic nature of open automata.
-Indeed, a single state of the automaton represents a potentially infinite number of concrete states, depending on the value of state variables, and a single open transition of the automaton may also be instantiated with an unbounded number of values for the transition parameters.
+Indeed, a single state of the automaton represents a potentially infinite number of concrete states, depending on the value of the automaton variables, and a single open transition of the automaton may also be instantiated with an unbounded number of values for the transition parameters.
 Consequently it would be too restrictive to impose that each transition of one automaton is matched by exactly one transition of the bisimilar automaton.
-Thus the definition of bisimulation requires that, for each open transition of one automaton, there exists a matching  set of open transitions covering the original one, indeed depending on the value of action parameters or state variables different open transitions might simulate the original one provided the reached states are bisimilar.
+Thus the definition of bisimulation requires that, for each open transition of one automaton, there exists a matching  set of open transitions covering the original one, indeed depending on the value of action parameters or automaton variables different open transitions might simulate the original one provided the reached states are bisimilar.
 
@@
 A FH-bisimulation relation maps pairs of states to boolean expressions that use variables of the two states.
-Each variable used in $\Pred_{s,t}$ should refer to a state variable of $s$ or $t$ and there must be no ambiguity on the referenced variable, we thus require that the two compared automata have disjoint state variables.
+%Each variable used in $\Pred_{s,t}$ should refer to a state variable of $s$ or $t$ and there must be no ambiguity on the referenced variable, we thus require that the two compared automata have disjoint state variables.
 Formally, a relation over the states of two open automata  $\mylangle J,\mathcal{S}_1, s_0,V_1,
@@
 We adopt a notation similar to standard relations and denote it
- $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$. 
-The relation $\mathcal{R}$ must verify the following constraints: 1) For any pair $(s,t)\in \mathcal{S}_1\times \mathcal{S}_2$, there is a 
+ $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$, where: 1) For any pair $(s,t)\in \mathcal{S}_1\times \mathcal{S}_2$, there is a 
    single
@@
       if $\Pred_{s,t}$       is 
-      True, i.e.
-the states are related when the value of the variables in $s$ and $t$  verify the predicate $\Pred_{s,t}$.
+      True, i.e. the states are related when the value of the automata variables% in $s$ and $t$
+  verify the predicate $\Pred_{s,t}$.
 2) The free variables of  $\Pred_{s,t}$ belong to $V_1$ and $V_2$, i.e.
@@
 
-The definition of bisimulation for open automata allows us to derive the characterisation and properties of a
+The definition of bisimulation for open automata allows us to derive the characterization and properties of a
 bisimulation relation for open pNets. As pNets are composition
@@
 \end{definition}
-To be precise, the state of each pLTS is entirely characterised by both the state of the automaton, and the value of its variables $V$.
+To be precise, the state of each pLTS is entirely characterized by both the state of the automaton, and the value of its variables $V$.
 Consequently, the complete characterization of the state of a pNet should take into account the value of its variables $vars(P)$.
@@
 on some kinds of labelled transition systems.
-The distinguishing feature of their approach is the transitions systems are labelled with logical formulae that provides  an abstract characterisation of the structure that a hole must possess and of the actions it can perform in order to allow a transition to fire.
+The distinguishing feature of their approach is the transitions systems are labelled with logical formulae that provides  an abstract characterization of the structure that a hole must possess and of the actions it can perform in order to allow a transition to fire.
 Logical formulae are suitable formats that capture the general class of components that can act as the placeholders of the system during its evolution.
@@
 \noindent ($\Leftarrow$) We proceed by structural induction on the rules  building  the weak transition (as described in the original definition).
-The recurrence hypothesis being that the  the original definition implies the characterisation (1),with the conditions stated at the bottom of the theorem.
+The recurrence hypothesis being that the  the original definition implies the characterization (1),with the conditions stated at the bottom of the theorem.
 We consider the different rules:
@@
 Indeed, we essentially use the same proof-scheme the main difference concerns  $\beta$ and  $\gamma$.
-Indeed, while the schema of the proof of transitivity was not directly applicable on the definition of weak bisimulation,  Lemma~\ref{lem-alternative-weak-bisim} provides a characterisation of weak bisimulation similar to the definition of strong bisimulation, and thus the same proof scheme is directly applicable.
+Indeed, while the schema of the proof of transitivity was not directly applicable on the definition of weak bisimulation,  Lemma~\ref{lem-alternative-weak-bisim} provides a characterization of weak bisimulation similar to the definition of strong bisimulation, and thus the same proof scheme is directly applicable.
 

### 2021-09-21 2016-Weak-FH-Bisim/WeakBisim.tex
passe apres relecture

@@
 Classical bisimulations require to exhibit, for each transition of one system, a transition of the other system that simulates it.
-Instead, bisimulation for open automata  rely on the simulation of each open transition of one automaton by a set of open transitions of the other one, that should cover all the
+Instead, bisimulation for open automata  relies on the simulation of each open transition of one automaton by a set of open transitions of the other one, that should cover all the
 cases where the original transition can be triggered.
@@
 %by the additional assignments.
-\item[$\bullet$] $V$ is a set of global variables for the pLTS,
+\item[$\bullet$] $V$ is a set of global variables for the pLTS.
 \item[$\bullet$] $\to \subseteq S \times L \times S$ is the transition relation and 
@@
 
-\item[$\bullet$] $J$ is a set of indexes, called \emph{holes}.
-$I$ and $J$ are \emph{disjoint}: $I\!\cap\! J=\emptyset$,  $I\!\cup\! J\neq\emptyset$
+\item[$\bullet$] $J$ is a set of indices, called \emph{holes}.
+$I$ and $J$ are \emph{disjoint}: $I\!\cap\! J=\emptyset$,  $I\!\cup\! J\neq\emptyset$.
 \item[$\bullet$] $\Sort_j \subseteq \AlgAS$  is a set of action terms, denoting the 
@@
 The set of holes $\Holes(\pNet)$ of a pNet is the indices of the holes of the pNet 
-itself plus the indexes of all the holes of its sub-pNets.
-It is defined inductively (we suppose those indexes 
+itself plus the indices of all the holes of its sub-pNets.
+It is defined inductively (we suppose those indices 
 disjoints):
@@
 is said to be \emph{open}.
-Sort come naturally with a compatibility relation that is similar to a type-compatibility check.
+Sort comes naturally with a compatibility relation that is similar to a type-compatibility check.
 We simply say that two sorts are compatible if they consist of the same actions with the same arity.
@@
 pNets are composition entities equipped with a rich synchronisation mechanism: synchronisation vectors allow the expression of synchronisation between any number of entities and at the same time the passing of data between processes.
-Their strongest feature is that the data emitted by processes can be used can be used inside the synchronisation vector to do addressing: it is easy to synchronise a process indexed by $n$ with the action $a(v,n)$ of another process.
+Their strongest feature is that the data emitted by processes can be used  inside the synchronisation vector to do addressing: it is easy to synchronise a process indexed by $n$ with the action $a(v,n)$ of another process.
 This is very convenient to model systems and encode futures or message routing.
@@
 Consequently, much of the formalisation efforts did not use holes and the interplay between holes, sorts, and synchronisation vector was not formalised.
-In previous works~\cite{AmeurBoulifa2017}, only closed pNets were equipped with a semantics, it was defined as an instantiation of labelled transition systems.
-The old semantics is not necessary to understand this article but it defines the semantics of pNets in a simpler and more operational setting.
+In previous works~\cite{AmeurBoulifa2017}, only closed pNets were equipped with a semantics, it was defined as labelled transition systems which are instantiations of pNets. 
+%The old semantics is not necessary to understand this article but it defines the semantics of pNets in a simpler and more operational setting. 
 The theory of pNets as operators able to fully take into account open systems is given in the following sections.
@@
 The pNet has a tree-like structure.
-The root node of the tree {\it SimpleSystemSpec} is the top level of the pNet structure.
+The root node of the tree {\it SimpleSystem} is the top level of the pNet structure.
 It acts as the parallel operator.
-It consists of three nodes: two holes $P$ and $Q$ and one sub-pNet, denoted {\it PrefectBuffer}.
+It consists of three nodes: two holes $P$ and $Q$ and one sub-pNet, denoted {\it PerfectBuffer}.
 Nodes of the tree are synchronized using four synchronization vectors, that  express the possible synchronizations between the parameterised actions of a subset of the nodes.
-For instance, in the vector "$< \texttt{p-send(m)},\texttt{in(m)},\_> \rightarrow \texttt{\nounderline{in(m)}}$" only $P$ and {\it PrefectBuffer} nodes are involved in the synchronization.
-The synchronization between these processes occurs when  process $P$  performs $\texttt{p-send(m)}$  action sending a message, and  the {\it PrefectBuffer} accepts the message through an $\texttt{in(m)}$ action  at the same time; the result that will be returned at upper level is the action  $\texttt{\nounderline{in(m)}}$.
+For instance, in the vector $< \texttt{p-send(m)},\texttt{in(m)},\_> \rightarrow \texttt{\nounderline{in(m)}}$ only $P$ and {\it PerfectBuffer} nodes are involved in the synchronization.
+The synchronization between these processes occurs when  process $P$  performs $\texttt{p-send(m)}$  action sending a message, and  the {\it PerfectBuffer} accepts the message through an $\texttt{in(m)}$ action  at the same time; the result that will be returned at upper level is the action  $\texttt{\nounderline{in(m)}}$.
 
@@
    \includegraphics[width=.62\textwidth]{XFIG/SimpleProt2-Spec.pdf}
-   \caption{pNet structure of the example and specification expressed as a pNet}
+   \caption{pNet structure of the example and its specification expressed as a pNet}
    \label{SimpleProt:Spec}
-
 \end{figure}
+
+In the following, we refer to the automaton of a specification by $\symb{Spec}$ and of an implementation by $\symb{Impl}$.
 
@@
   \centerline{\includegraphics[width=.95\textwidth]{XFIG/SimpleProt2-pNet-tau}}
-  \caption{Composed pNet with the Simple Protocol Implementation}  \label{SimpleProt:Impl}
+  \caption{The $\symb{SimpleSystem}$ composed with the $\symb{Impl}$ of $\symb{SimpleProtocol}$}  \label{SimpleProt:Impl}
 \end{figure}
@@
 This section defines open automata and a bisimulation theory for them.
-This section can be viewed as an improved version of the formalism described in \cite{henrio:Forte2016}, extending the automata with a notion of global variable, which makes the state of the automaton more explicit.
+This section is an improved version of the formalism described in \cite{henrio:Forte2016}, extending the automata with a notion of global variable, which makes the state of the automaton more explicit.
 We also adopt a semantics and logical interpretation of the automata that intuitively can be stated as follows: ``if a transition belongs to an open automaton, any refinement of this transition also belongs to the automaton''.
@@
 	Where $J'\subseteq J$ is the set of holes involved in the transition; $s, s'\in\mathcal{S}$ are states of the automaton; and $\beta_j$
-        is a transition of the hole $j$, with $\Sortop(\beta_j)\in\Sort_j$. $\alpha$ is an action 
+        is a transition of the hole $j$, with $\Sortop(\beta_j)\in\Sort_j$. $\alpha$ \TODO{$\beta_j\in\Sort_j$ -- Pourquoi utiliser Sort d'un trou} is an action 
         label denoting the resulting action of this open transition. 
@@
         \Pred\ is a predicate over the  variables in $V\cup\vars(\alpha)\cup
-			{\displaystyle \bigcup_{j\in J'}\vars(beta_j)}$. \Post\ is a set of 
+			{\displaystyle \bigcup_{j\in J'}\vars(\beta_j)}$. \Post\ is a set of 
 	assignments that are effective after the open transition, they are
@@
         over the variables variables in $V\cup\vars(\alpha)\cup
-			{\displaystyle \bigcup_{j\in J'}\vars(beta_j)}$.
+			{\displaystyle \bigcup_{j\in J'}\vars(\beta_j)}$.
 The assignments are always applied simultaneously because the variables in $V$ can be in both sides ($x_k$s are distinct).
@@
 
-It is important to understand the difference between the red dotted rule and a normal 
+It is important to understand the difference between the red dotted rule and a classical 
 inference rule. They correspond to two different logical levels.
@@
 		\item[$\bullet$] $\mathcal{T}$ is a set of open transitions and for each
-		$t\in \mathcal{T}$ there exist  $J'$ with  $J'
+		$t\in \mathcal{T}$ there exists  $J'$ with  $J'
 		\subseteq J$, such that $t$ is an open transition over  $J'$
@@
 Because of the semantic interpretation of open automata, the set of open transition of an open automaton is infinite (for example because every free variable can be renamed).
-However an open automaton is characterized by a  subset of these open transition which is sufficient to generate, by substitution the other ones.
+However an open automaton is characterized by a  subset of these open transitions which is sufficient to generate, by substitution the other ones.
 In the following, we will abusively write that we define an ``open automaton'' when we provide only the set of open transitions that is sufficient to generate a proper open automaton by saturating each open transition by all possible substitutions and refinements.
@@
 The equivalence we need is a strong bisimulation between
-open automata having exactly the same holes (same indexes and same sorts), but using a
+open automata having exactly the same holes (same indices and same sorts), but using a
 flexible matching 
@@
 
-We define now a bisimulation relation adapted to open automata and their parametric nature.
-This relation relates states of the open automaton and states equivalence between the open transitions between the states.
-Its key characteristics are 1) the introduction of predicates in the bisimulation relation: as states may contain variables, relation between states may depend on the value of the variables; 2) the bisimulation property relates elements of the open transitions and takes into account predicates over variables, actions of the holes, and state modifications.
+We define now a bisimulation relation tailored to open automata and their parametric nature.
+\TODO{This relation relates states of the open automaton and states equivalence between the open transitions between the states.!?} Its key characteristics are 1) the introduction of predicates in the bisimulation relation: as states may contain variables, relation between states may depend on the value of the variables; 2) the bisimulation property relates elements of the open transitions and takes into account predicates over variables, actions of the holes, and state modifications.
  We name it FH-bisimulation,
@@
 \end{mathpar}
- there exist an indexed set of  open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
+ there exists an indexed set of  open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
  \begin{mathpar}
@@
 predicate $\Predsv$ relating
-the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
+the actions of the involved sub-pNets and the resulting actions. \TODO{This predicate verifies -- A revoir}:
 \[\begin{array}{l}\Predsv \Big(\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
@@
 
-Note that  the construction is symbolic, and each open-transition deduced expresses a whole family of
+Note that  the construction is symbolic, and each open transition deduced expresses a whole family of
 behaviours, for any possible value of the variables.
@@
 
-In \cite{henrio:Forte2016}, we have shown a detailed example of the construction of a complex open transition, building a deduction tree using rules \TrUn ~and \TrDeux.
+In \cite{henrio:Forte2016}, we have also shown a detailed example of the construction of a complex open transition, building a deduction tree using rules \TrUn ~and \TrDeux.
 
@@
    \centerline{\includegraphics[width=13cm]{XFIG/SPSpecOpen}}
-   \caption{Specification Open Automaton}
+   \caption{$\symb{Spec}$ of $\symb{SimpleProtocol}$}
    \label{SimpleProtCounter:SpecOA}
@@
 
-\subsection*{Example}  Figure~\ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the Specification pNet given in Figure \ref{SimpleProt:Spec}. 
+\subsection*{Example}  Figure~\ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the specification pNet given in Figure \ref{SimpleProt:Spec}. 
 For later references, we give to the transitions of this (strong)
-Specification automaton as $SS_i$ while transitions of the
-Implementation automaton will be labelled $SI_i$. In the figure we
+specification automaton as $SS_i$ while transitions of the
+implementation automaton will be labelled $SI_i$. In the figure we
 have annotated each global state with the set of corresponding pLTS variables.
@@
   \centerline{\includegraphics[width=15cm]{XFIG/SPImplOpen}}
-  \caption{Open Automaton of the Simple Protocol Implementation}  \label{SimpleProtCounter:ImplOA}
+  \caption{$\symb{Impl}$ of $\symb{SimpleProtocol}$}  \label{SimpleProtCounter:ImplOA}
 \end{figure}
@@
 The resulting behaviour is quite simple:  we have a main loop including receiving a message from $P$ and transmitting the same message to $Q$, with some intermediate $\tau$ actions from the internal communications between the protocol processes.
-In most of the transitions, you can observe that data is propagated between the successive plts variables (holding the message, and the error counter value).
+In most of the transitions, you can observe that data is propagated between the successive pLTS variables (holding the message, and the error counter value).
 On the right of the figure, you have a loop of $\tau$ actions ($\texttt{SI}_4$, $\texttt{SI}_5$ and $\texttt{SI}_6$)  showing the handling of errors and corresponding increments of the error counter.
@@
 \begin{lemma}[Open transition decomposition\label{lem-decompose}] Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$}.
-	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose:
+	Let $\Leaves(Q)=p_l^{l\in L_Q}$ and suppose:
 	\[ P[Q]_{j_0}  
@@
 an open transition of $Q$, and building a corresponding transition of
-$P[Q]_{j_0}$, assembling their predicates.
+$P[Q]_{j_0}$ \TODO{assembling their predicates -- Pourquoi parler que predicats}.
 
@@
 Note also that $\beta_{j_0}$ is  only used as an intermediate term inside formulas in the composed open transition: it 
-does not appear neither as global action nor as an action of a hole.
+does not appear as global action, and will not appear as an action of a hole.
 
@@
 The first statement of the definition states that the open automaton must allow a hole to do a silent action at any time, and must not observe it, i.e.
-cannot change its internal state because a hole did a $\tau$ transition.
-The second statement ensures that there cannot be in the open automaton other transitions that would be able to observe a $\tau$ action from a hole: statement (2) states that all the open transitions where a hole does  a $\tau$ must be of the shape given in statement (1).
+it cannot change its internal state because a hole did a $\tau$ transition.
+The second statement ensures that there cannot be in the open automaton other transitions that would be able to observe a $\tau$ action from a hole: statement (2) states that all the open transitions where a hole does  a $\tau$ action must be of the shape given in statement (1).
 The condition $J=\{j\}$ is a bit restrictive, it could safely be replaced by $\forall j\in J.\, \beta_j=\tau$, allowing the other holes to perform $\tau$ transitions too (because these $\tau$ actions cannot be observed).

### 2021-09-21 2016-Weak-FH-Bisim/WeakBisim.tex
passe apres relecture +

@@
 	Where $J'\subseteq J$ is the set of holes involved in the transition; $s, s'\in\mathcal{S}$ are states of the automaton; and $\beta_j$
-        is a transition of the hole $j$, with $\Sortop(\beta_j)\in\Sort_j$. $\alpha$ \TODO{$\beta_j\in\Sort_j$ -- Pourquoi utiliser Sort d'un trou} is an action 
+        is a transition of the hole $j$, with \hl{$\Sortop(\beta_j)\in\Sort_j$. $\alpha$}  is an action 
         label denoting the resulting action of this open transition. 
@@
 
-While the definition and usage of the open transition can be formalised and taken in a pure syntactic acceptation, we take in this article a semantics and logical understanding of open automata. 
+While the definition and usage of the open transition can be formalised and taken in a pure syntactic acceptance, we take in this article a semantics and logical understanding of open automata. 
 Formally, the open transition sets in open automata are closed by a simple form of refinement that
@@
 We define now a bisimulation relation tailored to open automata and their parametric nature.
-\TODO{This relation relates states of the open automaton and states equivalence between the open transitions between the states.!?} Its key characteristics are 1) the introduction of predicates in the bisimulation relation: as states may contain variables, relation between states may depend on the value of the variables; 2) the bisimulation property relates elements of the open transitions and takes into account predicates over variables, actions of the holes, and state modifications.
+\hl{This relation relates states of the open automaton and states equivalence between the open transitions between the states.!?} Its key characteristics are 1) the introduction of predicates in the bisimulation relation: as states may contain variables, relation between states may depend on the value of the variables; 2) the bisimulation property relates elements of the open transitions and takes into account predicates over variables, actions of the holes, and state modifications.
  We name it FH-bisimulation,
@@
 predicate $\Predsv$ relating
-the actions of the involved sub-pNets and the resulting actions. \TODO{This predicate verifies -- A revoir}:
+the actions of the involved sub-pNets and the resulting actions. \hl{This predicate verifies}:
 \[\begin{array}{l}\Predsv \Big(\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
@@
 an open transition of $Q$, and building a corresponding transition of
-$P[Q]_{j_0}$ \TODO{assembling their predicates -- Pourquoi parler que predicats}.
+$P[Q]_{j_0}$ \hl{assembling their predicates}.
 

### 2021-09-22 2016-Weak-FH-Bisim/WeakBisim.tex
meeting notes

--- 2021-09-21 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 \usepackage{lmodern}
-%\usepackage{geometry}                % See geometry.pdf to learn the layout
+%\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
 %\geometry{a4paper}                   % ... or a4paper or a5paper or ...
@@
 
-Establishing equivalences between programs or systems is crucial both for verifying correctness of programs, by establishing that two implementations are equivalent, and for justifying optimisations and program transformations, by establishing that a modified program is equivalent to the source one.
+Establishing equivalences between programs or system is crucial both for verifying correctness of programs, by establishing that two implementations are equivalent, and for justifying optimisations and program transformations, by establishing that a modified program is equivalent to the source one.
 There exist several equivalence relations for programs, and bisimulations are among the most versatile of these equivalences.
-Among bisimulation relations one distinguishes strong bisimulation, that requires that each action of a program is simulated by a single action of the equivalent program, a weak bisimulation that  is a coarser relation, allowing some of the actions to be
+Among bisimulation relations one distinguishes strong bisimulation, that requires that each action of a program is simulated by a single action of the equivalent program, a weak bisimulation that  is a coarser relations, allowing some of the actions to be
   invisible or internal moves, and thus not simulated by the equivalent program.
@@
 transitions~\cite{deSimone85,Larsen87}. 
-These works use the term \emph{parameter} to designate systems where variables defining the system have a strong influence on their behaviour: in parameterised systems, parameters can typically influence the number of processes in the system or the way they interact.
+These works use the term \emph{parameter} to designate systems where variables defining the system as a strong influence on their behaviour: in parametrised systems, parameters can typically influence the number of processes in the system or the way they interact.
 In \cite{IngolfsdottirL:2001,HennessyLin:TCS95}, Lin, Ingolfsdottir and Hennessy developed a full hierarchy of
@@
 \subsubsection*{pNets and open automata}
-pNets is a convenient model to model concurrent systems in a hierarchical and parameterised way.
-The coordination between processes is expressed as synchronisation vectors that allow the definition of complex and expressive synchronisation patterns.
-Open pNets are pNets for which some elements in the hierarchy are still undefined, such undefined elements are called \emph{holes}; a hole can be \emph{filled} later by providing another pNet.
- The semantics of pNets can be expressed as a translation to a labelled transition system, but only if the pNet has no parameter and no holes.
+pNets is a convenient model to model concurrent systems in a hierarchical and parametrised way.
+The coordination between processes is expressed as synchronisation vectors that allows the definition of complex and expressive synchronisation patterns.
+open pNets are pNets for which one of the element in the hierarchy is still undefined, such undefined element is called \emph{hole}; a hole can be \emph{filled} later by providing another pNet.
+ The semantics of pNets can be expressed as a translation to a labelled transition system, but only if the pNet has no parameter or it has holes.
 Adding parameters to a LTS is quite standard but enabling holes inside LTSs is not a well-defined notion.
@@
 
-Contrarily to pNets, open automata are not hierarchical structures, thus they are more convenient for formal reasoning but not adapted to the definition of a complex and structured system like pNets.
-Additionally, open transitions are expressed in terms of logics more than in terms of synchronised actions, synchronisation vectors on the contrary make it easy to express synchronisations that exist in process algebra orin specification and high-level languages for distributed systems.
-
-This article defines pNets and illustrates with an example how they can be used to provide the model of a communicating system.
+Contrarily to pNets, open automata are not hierarchical structure, thus they are more convenient for formal reasoning but not adapted to the definition of a complex and structured system like pNets.
+Additionally, open transitions are expressed in terms of logics more than in terms of synchronised actions, synchronisation vectors on the contrary make it easy to express synchronisations that exist in process algebra or distributed systems.
+
+This article defines pNets and illustrate with an example how they can be used to provide the model of a communicating system.
 Then we introduce open automata to provide a semantics to open pNets and introduce bisimulation relations and their properties.
-Open automata can be also seen as an algebra that can be studied independently from its application to pNets but their composition properties make more sense in a hierarchical model like pNets.
+Open automata can be also seen as an algebra that can be studied independently from its application to pNets but the composition properties make more sense in a hierarchical model like pNets.
 
@@
 One of the original aspects of FH-bisimulation is due to the symbolic nature of open automata.
-Indeed, a single state of the automaton represents a potentially infinite number of concrete states, depending on the value of the automaton variables, and a single open transition of the automaton may also be instantiated with an unbounded number of values for the transition parameters.
+Indeed, a single state of the automaton represents a potentially infinite number of concrete states, depending on the value of state variables, and a single open transition of the automaton may also be instantiated with an unbounded number of values for the transition parameters.
 Consequently it would be too restrictive to impose that each transition of one automaton is matched by exactly one transition of the bisimilar automaton.
-Thus the definition of bisimulation requires that, for each open transition of one automaton, there exists a matching  set of open transitions covering the original one, indeed depending on the value of action parameters or automaton variables different open transitions might simulate the original one provided the reached states are bisimilar.
+Thus the definition of bisimulation requires that, for each open transition of one automaton, there exists a matching  set of open transitions covering the original one, indeed depending on the value of action parameters or state variables different open transitions might simulate the original one provided the reached states are bisimilar.
 
@@
 A FH-bisimulation relation maps pairs of states to boolean expressions that use variables of the two states.
-%Each variable used in $\Pred_{s,t}$ should refer to a state variable of $s$ or $t$ and there must be no ambiguity on the referenced variable, we thus require that the two compared automata have disjoint state variables.
+Each variable used in $\Pred_{s,t}$ should refer to a state variable of $s$ or $t$ and there must be no ambiguity on the referenced variable, we thus require that the two compared automata have disjoint state variables.
 Formally, a relation over the states of two open automata  $\mylangle J,\mathcal{S}_1, s_0,V_1,
@@
 We adopt a notation similar to standard relations and denote it
- $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$, where: 1) For any pair $(s,t)\in \mathcal{S}_1\times \mathcal{S}_2$, there is a 
+ $\mathcal{R}=\{(s,t|\Pred_{s,t})\}$. 
+The relation $\mathcal{R}$ must verify the following constraints: 1) For any pair $(s,t)\in \mathcal{S}_1\times \mathcal{S}_2$, there is a 
    single
@@
       if $\Pred_{s,t}$       is 
-      True, i.e. the states are related when the value of the automata variables% in $s$ and $t$
-  verify the predicate $\Pred_{s,t}$.
+      True, i.e.
+the states are related when the value of the variables in $s$ and $t$  verify the predicate $\Pred_{s,t}$.
 2) The free variables of  $\Pred_{s,t}$ belong to $V_1$ and $V_2$, i.e.
@@
 
-The definition of bisimulation for open automata allows us to derive the characterization and properties of a
+The definition of bisimulation for open automata allows us to derive the characterisation and properties of a
 bisimulation relation for open pNets. As pNets are composition
@@
 \end{definition}
-To be precise, the state of each pLTS is entirely characterized by both the state of the automaton, and the value of its variables $V$.
+To be precise, the state of each pLTS is entirely characterised by both the state of the automaton, and the value of its variables $V$.
 Consequently, the complete characterization of the state of a pNet should take into account the value of its variables $vars(P)$.
@@
       \begin{multline*}
-\forall fv_{OT}.\, \Big\{ \Pred \land \Pred_{OT} \implies\\
+\forall fv_{OT}.\, \Big\{ \Pred_{s,t} \land \Pred_{OT} \implies\\
  \bigvee_{x\in X}\!
@@
 on some kinds of labelled transition systems.
-The distinguishing feature of their approach is the transitions systems are labelled with logical formulae that provides  an abstract characterization of the structure that a hole must possess and of the actions it can perform in order to allow a transition to fire.
+The distinguishing feature of their approach is the transitions systems are labelled with logical formulae that provides  an abstract characterisation of the structure that a hole must possess and of the actions it can perform in order to allow a transition to fire.
 Logical formulae are suitable formats that capture the general class of components that can act as the placeholders of the system during its evolution.
@@
 \noindent ($\Leftarrow$) We proceed by structural induction on the rules  building  the weak transition (as described in the original definition).
-The recurrence hypothesis being that the  the original definition implies the characterization (1),with the conditions stated at the bottom of the theorem.
+The recurrence hypothesis being that the  the original definition implies the characterisation (1),with the conditions stated at the bottom of the theorem.
 We consider the different rules:
@@
 Indeed, we essentially use the same proof-scheme the main difference concerns  $\beta$ and  $\gamma$.
-Indeed, while the schema of the proof of transitivity was not directly applicable on the definition of weak bisimulation,  Lemma~\ref{lem-alternative-weak-bisim} provides a characterization of weak bisimulation similar to the definition of strong bisimulation, and thus the same proof scheme is directly applicable.
+Indeed, while the schema of the proof of transitivity was not directly applicable on the definition of weak bisimulation,  Lemma~\ref{lem-alternative-weak-bisim} provides a characterisation of weak bisimulation similar to the definition of strong bisimulation, and thus the same proof scheme is directly applicable.
 

### 2021-09-22 2016-Weak-FH-Bisim/WeakBisim.tex
corrected one highlighted dsentence

--- 2021-09-21 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 We define now a bisimulation relation tailored to open automata and their parametric nature.
-\hl{This relation relates states of the open automaton and states equivalence between the open transitions between the states.!?} Its key characteristics are 1) the introduction of predicates in the bisimulation relation: as states may contain variables, relation between states may depend on the value of the variables; 2) the bisimulation property relates elements of the open transitions and takes into account predicates over variables, actions of the holes, and state modifications.
+This relation relates states of the open automaton and guarantees that the related states are observationally equivalent, i.e.
+equivalent states can trigger transitions with identical action labels.
+Its key characteristics are 1) the introduction of predicates in the bisimulation relation: as states may contain variables, relation between states may depend on the value of the variables; 2) the bisimulation property relates elements of the open transitions and takes into account predicates over variables, actions of the holes, and state modifications.
  We name it FH-bisimulation,

### 2021-09-29 2016-Weak-FH-Bisim/WeakBisim.tex
add 2 sentences on GSOS, and 2 bob refs

@@
 We develop here a semantics for a model of interacting processes with parameters and holes. 
+Our approach is originaly inspired from Structured Operational Semantics with conditional premisses as in \cite{GROOTE1993263,VANGLABBEEK2004229}.
+But we aim at a more constructive and implementable appraoch to compute the semantics (intuitively transitions including first order predicates) and to 
+check equivalences for these open systems.
 The main interest of our symbolic approach is to define a method to
@@
  A classical relation between states can be seen as a function mapping pairs of state to a boolean value (true if the states are related, false if they are not).
-A FH-bisimulation relation maps pairs of states to boolean expressions that use variables of the two states.
+A FH-bisimulation relation maps pairs of states to boolean expressions that use variables of the two systems.
 %Each variable used in $\Pred_{s,t}$ should refer to a state variable of $s$ or $t$ and there must be no ambiguity on the referenced variable, we thus require that the two compared automata have disjoint state variables.
@@
 This section defines the semantics of an open pNet as a translation into an open automaton. 
-In this translation, the states of the open automata are obtained from
+In this translation, the states of the open automata are obtained as products of 
 the states of the pLTSs at the leaves of the composition. The
@@
 \subsection{Deriving an open automaton from an open pNet}
-To derive an open automaton from a pNet, we need to describe the set of states of the automaton, and then we will detail the construction rule for transitions of the automaton, this will rely on the derivation of predicate unifying synchronisation vectors and the actions of the pNets involved in a given synchronisation.
+To derive an open automaton from a pNet, we need to describe the set of states of the automaton, and then we will detail the construction rule for transitions of the automaton, this will rely on the derivation of predicates unifying synchronisation vectors and the actions of the pNets involved in a given synchronisation.
 

### 2021-09-29 2016-Weak-FH-Bisim/WeakBisim.tex
petit topo Raffinement

@@
 In the case of interaction protocols~\cite{BHHM:FACS11}, composition of bisimulation can justify abstractions used in some parts of the application.
+
+pNets have through composition  the ability both to add new holes to a system and to fill holes, obtaining a system with less holes.
+They support the refinement checking at the automata level through a simulation approach, with symbolic evaluation of
+the guards and transitions.
+The definition of simulation on open automata should be  stronger than a strict simulation since it matches a transition with a family of transitions.
+Such a relation should be able to check the refinement between two open automata with the same level of abstraction but specified differently, for example, by duplicating states, removing transitions, reinforcing guards, modifying variables.
+But it also should  support the  comparison of automata that do not have the same number of holes.
 

### 2021-09-29 2016-Weak-FH-Bisim/WeakBisim.tex
changed end of conclusion (tools et work in progress)
manque encore refbib "SMC"

--- 2021-09-29 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 developed algorithms to check strong FH-bisimulation \cite{hou:hal-02406098}.
-Naturally we are now working toward an implementation of weak FH-Bisimulation. 
+More reecntly we published preliminary work for the case of weak FH-Bisimulation \cite{}. 
 The challenges here, in the context of our symbolic systems, is not so much algorithmic complexity,
 as was the case with classical weak bisimulation on finite models, but decidability and termination.
-Two main directions should be explored, either with an explicit construction of the weak transition, but this step in
-itself may introduce non-termination, or a direct implementation of the weak bisimulation definition, without
-constructing the weak automaton. We can expect that optimisations here in the symbolic setting would be quite different from the classical case.
+The naive approach using an explicit construction of the weak transition, may in itself introduce non-termination,
+so we prefer a direct implementation of the weak bisimulation definition, without
+constructing the weak automaton, but searching \emph{on demand} to construct the required weak transitions.
+Alternatively, we explore more pragmatic approaches using weak bisimulation preserving (pattern-based) 
+reduction rules \cite{wang:hal-03126313}.
 

### 2021-09-30 2016-Weak-FH-Bisim/WeakBisim.tex
ajoute un paragraphe sur les formats de regles dans "related work"

@@
 Defining properly the interaction between a logical formulae in the action and the logics of the pNet composition seems very difficult.
+
+There is also a clear relation with the seminal works on rule formats for Structured Operational Semantics, e.g.
+DeSimone format, GSOS, and conditional rules with or without negative premisses \cite{deSimone85,Bloom88bisimulationcant,GROOTE1992202,VANGLABBEEK2004229}.
+Open pNets provides a way to define operators similar to these rules formats, but with quite different aim and approach.
+A formal comparison would be interesting, though not trivial.
+What we can say easily is that: the pNet format syntactically encompasses both DeSimone, GSOS, and conditional premisses rules.
+Then our compositionality result is more powerful than the classical result, but this is not a surprise, as it relies on a (sufficient) syntactic hypothesis on particular systems, rather than the general rules defining an operator.
+Last, we intentionaly do not accept negative premisses, that would be more diffcult to put into practice in our implementation.
 

### 2021-10-01 2016-Weak-FH-Bisim/WeakBisim.tex
a paragraph on difference with process algebras

@@
 
+\paragraph{What is new about open automata bisimulation?}
+
 Bisimulation over a symbolic and open model like open pNets or open automata is  different from the classical notion of bisimulation because it cannot rely on the equality over a finite set of action labels.
@@
 cases where the original transition can be triggered.
+
+Compositionality of bisimulation in our model come from the specification of the interactions, including actions of the holes.
+In pNets synchronisation vectors define the possible interactions between the pNet that fills the hole and the surrounding pNets.
+In open automata, this is reflected by symbolic hypotheses that depend on the actions of the holes.
+This additional specification is the price to pay to obtain the compositionality of bisimulation that cannot be guaranteed in traditional process algebras.
+
+This approach also allows us to specify a sufficient condition on allowed transitions to make weak bisimulation compositional; namely it is not possible to synchronise on invisible actions from the holes or prevent them to occur.
 

### 2021-10-01 2016-Weak-FH-Bisim/WeakBisim.tex
predicate

@@
 
-\paragraph{What is new about open automata bisimulation?}
+\subsubsection*{What is new about open automata bisimulation?}
 
@@
 %be a pNet. 
-Consider a synchronisation vector $\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
+ We 
+define a
+predicate $\Predsv$ relating a synchronisation vector (of the form $\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
 {\alpha'} 
-{e_b}$. We 
-define a
-predicate $\Predsv$ relating
-the actions of the involved sub-pNets and the resulting actions. \hl{This predicate verifies}:
-\[\begin{array}{l}\Predsv \Big(\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
+{e_b}$),
+the actions of the involved sub-pNets and the resulting actions.
+\TODO{rabea: check}
+ This predicate verifies:
+\[\begin{array}{l}\Predsv \Big(\left(\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
 {\alpha'} 
-{e_b}, \alpha_i^{i\in I}, \beta_j^{j\in J}, \alpha\Big)\Leftrightarrow \\~\qquad\qquad%\bigg(
+{e_b}\right), \alpha_i^{i\in I}, \beta_j^{j\in J}, \alpha\Big)\Leftrightarrow \\~\qquad\qquad%\bigg(
 %
@@
 
+\TODO{relire}
 We are currently extending this work,  looking at further properties of FH-bisimulation, but also

### 2021-10-01 2016-Weak-FH-Bisim/WeakBisim.tex
a new abstract

@@
 
-pNets is a generalisation of automata that includes variables and hierarchical composition.
+pNets is a generalisation of automata that model open systems.
+They features variables and hierarchical composition.
 Open pNets are pNets with holes, i.e.
 placeholders inside the hierarchical structure  that can be filled by sub-systems.
-Reasoning on open pNets allows us to reason on open systems.
-  Open pNets have a notion of \emph{synchronised actions}
-  generalizing the usual internal actions (e.g. $\tau$ of CCS, or $i$
-  in Lotos).
+%  Open pNets have a notion of \emph{synchronised actions}
+%  generalizing the usual internal actions (e.g. $\tau$ of CCS, or $i$
+%  in Lotos).
 
@@
   In practice, as happens in process algebras, strong bisimulation is too strong, and
-  we need to define some coarser relations, taking into account
+  we define some coarser relations, taking into account
   invisible or internal moves.
@@
 Among these properties we are interested in compositionality: If two systems are proven equivalent they will be undistinguishable by their context, and they will also be undistinguishable when their holes are filled with equivalent systems.
+We identify sufficient conditions on the automata to ensure compositionality of strong and weak bisimulation.
 The article is illustrated with a transport protocol running example; it shows the characteristics of our formalism and our bisimulation relations.

### 2021-10-01 2016-Weak-FH-Bisim/WeakBisim.tex
a few corrections in intro

@@
 transitions~\cite{deSimone85,Larsen87}. 
-These works use the term \emph{parameter} to designate systems where variables defining the system have a strong influence on their behaviour: in parameterised systems, parameters can typically influence the number of processes in the system or the way they interact.
+These works use the term \emph{parameter} to designate systems where variables that have a strong influence the system structure and behaviour.
+In parameterised systems, parameters can typically be the number of processes in the system or the way they interact.
 In \cite{IngolfsdottirL:2001,HennessyLin:TCS95}, Lin, Ingolfsdottir and Hennessy developed a full hierarchy of
@@
 Open pNets are pNets for which some elements in the hierarchy are still undefined, such undefined elements are called \emph{holes}; a hole can be \emph{filled} later by providing another pNet.
- The semantics of pNets can be expressed as a translation to a labelled transition system, but only if the pNet has no parameter and no holes.
+ The semantics of pNets can be expressed as a translation to a labelled transition system, but only if the pNet has no parameter and no hole.
 Adding parameters to a LTS is quite standard but enabling holes inside LTSs is not a well-defined notion.
@@
 Contrarily to pNets, open automata are not hierarchical structures, thus they are more convenient for formal reasoning but not adapted to the definition of a complex and structured system like pNets.
-Additionally, open transitions are expressed in terms of logics more than in terms of synchronised actions, synchronisation vectors on the contrary make it easy to express synchronisations that exist in process algebra orin specification and high-level languages for distributed systems.
+Additionally, open transitions are expressed in terms of logics more than in terms of synchronised actions, synchronisation vectors on the contrary make it easy to express synchronisations that exist in process algebra or in specification and high-level languages for distributed systems.
 
@@
 only a few entries we use the notation $(3\mapsto t)$ instead.
-Note that, sentences of the form ``there exists $t_i^{i\in I}$'' means there exists $I$ and a function that maps each element of $I$ to a term $t_i$.
+In this article, sentences of the form ``there exists $t_i^{i\in I}$'' means there exists $I$ and a function that maps each element of $I$ to a term $t_i$.
 %The operation  $A[j \mapsto a]$ updates the value associated to $j$ in map $A$ so that 
@@
 Note that a substitution is defined by a partial function that is applied on the variables inside a term.
-We let $\Post$ range over partial functions that are used as substitution and use the notation $\{y_i\gets e_i\}^{i\in I}$ to define such a partial function\footnote{Note that the fact that substitutions are defined from partial function  implies that each $y_i$ is different.}.
+We let $\Post$ range over partial functions that are used as substitution and use the notation $\{y_i\gets e_i\}^{i\in I}$ to define such a partial function\footnote{When using this notation, we suppose, without loss of generality that each $y_i$ is different.}.
 These partial functions are sometimes called \emph{substitution functions} in the following.
@@
 We simply say that two sorts are compatible if they consist of the same actions with the same arity.
-In practice, it is sufficient to check the equality of the two sets of pairs $(\alpha,n)$ of the two sorts.
+In practice, it is sufficient to check the equality of the two sets of pairs $(\alpha,n)$ of the two sorts\footnote{A more complex compatibility relation could be defined, but this is out of the scope of this article.}.
 \end{definition}

### 2021-10-05 2016-Weak-FH-Bisim/WeakBisim.tex
je pousse mes petites corrections de ce matin.

@@
 pNets is a generalisation of automata that model open systems.
-They features variables and hierarchical composition.
+They feature variables and hierarchical composition.
 Open pNets are pNets with holes, i.e.
-placeholders inside the hierarchical structure  that can be filled by sub-systems.
+placeholders inside the hierarchical structure  that can be filled later by sub-systems.
 %  Open pNets have a notion of \emph{synchronised actions}
@@
  We first define a strong bisimulation for open pNets.
-  In practice, as happens in process algebras, strong bisimulation is too strong, and
+ \TODO{virer cette phrase, doublon du 1er paragraph?} In practice, as happens in process algebras, strong bisimulation is too strong, and
   we define some coarser relations, taking into account
@@
   the classical \emph{weak bisimulation}, and study its properties.
-Among these properties we are interested in compositionality: If two systems are proven equivalent they will be undistinguishable by their context, and they will also be undistinguishable when their holes are filled with equivalent systems.
+Among these properties we are interested in compositionality: if two systems are proven equivalent they will be undistinguishable by their context, and they will also be undistinguishable when their holes are filled with equivalent systems.
 We identify sufficient conditions on the automata to ensure compositionality of strong and weak bisimulation.
@@
 DeSimone format, GSOS, and conditional rules with or without negative premisses \cite{deSimone85,Bloom88bisimulationcant,GROOTE1992202,VANGLABBEEK2004229}.
-Open pNets provides a way to define operators similar to these rules formats, but with quite different aim and approach.
+The Open pNets model provides a way to define operators similar to these rules formats, but with quite different aim and approach.
 A formal comparison would be interesting, though not trivial.
 What we can say easily is that: the pNet format syntactically encompasses both DeSimone, GSOS, and conditional premisses rules.
-Then our compositionality result is more powerful than the classical result, but this is not a surprise, as it relies on a (sufficient) syntactic hypothesis on particular systems, rather than the general rules defining an operator.
+Then our compositionality result is more powerful than their classical results, but this is not a surprise, as we rely on a (sufficient) syntactic hypothesis on a particular system, rather than the general rules defining an operator.
 Last, we intentionaly do not accept negative premisses, that would be more diffcult to put into practice in our implementation.
+an extension could be studied in future work.
 
@@
 developed algorithms to check strong FH-bisimulation \cite{hou:hal-02406098}.
-More reecntly we published preliminary work for the case of weak FH-Bisimulation \cite{}. 
+More recently we published preliminary work for the case of weak FH-Bisimulation \cite{}. 
 The challenges here, in the context of our symbolic systems, is not so much algorithmic complexity,
@@
 so we prefer a direct implementation of the weak bisimulation definition, without
-constructing the weak automaton, but searching \emph{on demand} to construct the required weak transitions.
-Alternatively, we explore more pragmatic approaches using weak bisimulation preserving (pattern-based) 
-reduction rules \cite{wang:hal-03126313}.
+constructing the weak automata, but searching \emph{on demand} to construct the required weak transitions.
+Beside, we explore in \cite{wang:hal-03126313} more pragmatic approaches using weak bisimulation preserving (pattern-based) 
+reduction rules.
 

### 2021-10-05 2016-Weak-FH-Bisim/WeakBisim.tex
petites correct aussi

@@
   \centerline{\includegraphics[width=.95\textwidth]{XFIG/SimpleProt2-pNet-tau}}
-  \caption{The $\symb{SimpleSystem}$ composed with the $\symb{Impl}$ of $\symb{SimpleProtocol}$}  \label{SimpleProt:Impl}
+  \caption{The $\symb{SimpleSystem}$ composed with the implementation of $\symb{SimpleProtocol}$}  \label{SimpleProt:Impl}
 \end{figure}
@@
 the actions of the involved sub-pNets and the resulting actions.
-\TODO{rabea: check}
+
  This predicate verifies:
@@
    \centerline{\includegraphics[width=13cm]{XFIG/SPSpecOpen}}
-   \caption{$\symb{Spec}$ of $\symb{SimpleProtocol}$}
+   \caption{Open Automaton of  $\symb{SimpleProtocolSpec}$}
    \label{SimpleProtCounter:SpecOA}
@@
   \centerline{\includegraphics[width=15cm]{XFIG/SPImplOpen}}
-  \caption{$\symb{Impl}$ of $\symb{SimpleProtocol}$}  \label{SimpleProtCounter:ImplOA}
+  \caption{Open Automaton of $\symb{SimpleProtocolImpl}$}  \label{SimpleProtCounter:ImplOA}
 \end{figure}
@@
 In the case of interaction protocols~\cite{BHHM:FACS11}, composition of bisimulation can justify abstractions used in some parts of the application.
-
-pNets have through composition  the ability both to add new holes to a system and to fill holes, obtaining a system with less holes.
-They support the refinement checking at the automata level through a simulation approach, with symbolic evaluation of
-the guards and transitions.
-The definition of simulation on open automata should be  stronger than a strict simulation since it matches a transition with a family of transitions.
-Such a relation should be able to check the refinement between two open automata with the same level of abstraction but specified differently, for example, by duplicating states, removing transitions, reinforcing guards, modifying variables.
-But it also should  support the  comparison of automata that do not have the same number of holes.
 
@@
    \centerline{\includegraphics[width=15cm]{XFIG/SPSpecWeakOpen}}
-  \caption{Weak Open Automaton of the Specification}
+  \caption{Weak Open Automaton of  $\symb{SimpleProtocolSpec}$}
    \label{SimpleProtCounter:WeakSpecOA}
@@
    \centerline{\includegraphics[width=11cm]{XFIG/SimpleProtImpl-WOA2}}
-  \caption{Weak Open Automaton of the implementation}
+  \caption{Weak Open Automaton of $\symb{SimpleProtocolImpl}$}
    \label{SimpleProtCounter:ImplWOA2}
@@
 \TODO{relire}
+pNets have through composition  the ability both to add new holes to a system and to fill holes, obtaining a system with less holes.
+They support the refinement checking at the automata level through a simulation approach, with symbolic evaluation of
+the guards and transitions.
+The definition of simulation on open automata should be  stronger than a strict simulation since it matches a transition with a family of transitions.
+Such a relation should be able to check the refinement between two open automata with the same level of abstraction but specified differently, for example, by duplicating states, removing transitions, reinforcing guards, modifying variables.
+But it also should  support the  comparison of automata that do not have the same number of holes.
+
 We are currently extending this work,  looking at further properties of FH-bisimulation, but also

### 2021-10-06 2016-Weak-FH-Bisim/WeakBisim.tex
work in the train: find impl references + imprvement + reading FW

@@
  We first define a strong bisimulation for open pNets.
- \TODO{virer cette phrase, doublon du 1er paragraph?} In practice, as happens in process algebras, strong bisimulation is too strong, and
+ \TODO{virer cette phrase, doublon du 1er paragraph? LUDO: OK} In practice, as happens in process algebras, strong bisimulation is too strong, and
   we define some coarser relations, taking into account
@@
 
-In the following, we refer to the automaton of a specification by $\symb{Spec}$ and of an implementation by $\symb{Impl}$.
+\TODO{remove this sentence: 
+In the following, we refer to the automaton of a specification by $\symb{Spec}$ and of an implementation by $\symb{Impl}$.}
 
@@
   \centerline{\includegraphics[width=.95\textwidth]{XFIG/SimpleProt2-pNet-tau}}
-  \caption{The $\symb{SimpleSystem}$ composed with the implementation of $\symb{SimpleProtocol}$}  \label{SimpleProt:Impl}
+  \caption{The $\symb{SimpleSystem}$ pNet composed with the implementation of $\symb{SimpleProtocol}$}  \label{SimpleProt:Impl}
 \end{figure}
@@
 %        $\beta_j$ and $\alpha$, and the state variables of $s$.
-        \Pred\ is a predicate over the  variables in $V\cup\vars(\alpha)\cup
-			{\displaystyle \bigcup_{j\in J'}\vars(\beta_j)}$. \Post\ is a set of 
+        \Pred\ is a predicate, \Post\ is a set of 
 	assignments that are effective after the open transition, they are
-        represented as a substitution function: $({x_k\gets e_k})^{k\in K}$ 
-	where $\forall k.\, x_k\in V$, and $e_k$ are expressions
-        over the variables variables in $V\cup\vars(\alpha)\cup
-			{\displaystyle \bigcup_{j\in J'}\vars(\beta_j)}$.
+        represented as a substitution function: $({x_k\gets e_k})^{k\in K}$.
+Predicates and expressions of an open transition can refer to the variables in $V$, and
+        in the different terms
+        $\beta_j$ and $\alpha$. More precisely:
+\[ \vars(\Pred) \subseteq V\cup\vars(\alpha)\cup
+			{\displaystyle \bigcup_{j\in J'}\!\!\vars(\beta_j)}\quad\land\quad
+\forall k.\, x_k\in V \land \vars(e_k)\subseteq V\cup\vars(\alpha)\cup
+			{\displaystyle \bigcup_{j\in J'}\!\!\vars(\beta_j)}\]
 The assignments are always applied simultaneously because the variables in $V$ can be in both sides ($x_k$s are distinct).
+
  Open transitions are identified
@@
 Consequently it would be too restrictive to impose that each transition of one automaton is matched by exactly one transition of the bisimilar automaton.
-Thus the definition of bisimulation requires that, for each open transition of one automaton, there exists a matching  set of open transitions covering the original one, indeed depending on the value of action parameters or automaton variables different open transitions might simulate the original one provided the reached states are bisimilar.
-
-The second original aspect is the nature of the bisimulation relation.
+Thus the definition of bisimulation requires that, for each open transition of one automaton, there exists a matching  set of open transitions covering the original one, indeed depending on the value of action parameters or automaton variables, different open transitions might simulate the same one.
+
+The parametric nature of the automata entails a second original aspect of FH-bisimulation : the nature of the bisimulation relation itself.
  A classical relation between states can be seen as a function mapping pairs of state to a boolean value (true if the states are related, false if they are not).
@@
    \mathcal{T}_1 \myrangle$ and $\mylangle J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2 \myrangle$ has the signature $\mathcal{S}_1\times\mathcal{S}_2\to\AlgB$. 
+We suppose without loss of generality that the variables of the two open automata are disjoint.
 We adopt a notation similar to standard relations and denote it
@@
       True, i.e. the states are related when the value of the automata variables% in $s$ and $t$
-  verify the predicate $\Pred_{s,t}$.
-2) The free variables of  $\Pred_{s,t}$ belong to $V_1$ and $V_2$, i.e.
-$\vars(\Pred_{s,t})\subseteq V_1\cup V_2$, and the variables of the two open automata are disjoint, i.e.
-$V_1\cap V_2=\emptyset$.
+  verify the predicate $\Pred_{s,t}$. 2) The free variables of  $\Pred_{s,t}$ belong to $V_1$ and $V_2$, i.e. $\vars(\Pred_{s,t})\subseteq V_1\cup V_2$.
  FH-bisimulation is defined formally: 
@@
    \mathcal{T}_1 \myrangle$ and $A_2 = \mylangle J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2 \myrangle$
-   are open automata with identical holes of the same sort, with disjoint sets of variables.
+   are open automata with identical holes of the same sort, with disjoint sets of variables ($V_1\cap V_2=\emptyset$).
 
@@
 \subsubsection*{Finite versus infinite open automata, and decidability:} 
-As mentioned in Definition \pageref{def:open-automaton}, we adopt here a semantic view on open automata. More precisely, in \cite{hou:hal-02406098}, we formerly define
+As mentioned in Definition \pageref{def:open-automaton}, we adopt here a semantic view on open automata. More precisely, in \cite{hou:hal-02406098}, we  define
 \emph{semantic open automata} (infinite as in Definition \ref{def:open-automaton}),
@@
     \smallskip
-    The global states here are triples, build as the product of states of the 3 pLTSs (remember the holes have no state). The assignment
-    $Post$ uses the variable $\texttt{m}$ from the action of hole $\texttt{P}$ to set the
+    The global states here are triples, the product of states of the 3 pLTSs (holes have no state). The assignment
+    performed by the open transition uses the variable $\texttt{m}$ from the action of hole $\texttt{P}$ to set the
     value of the sender variable named $\texttt{s\_msg}$.
@@
 
-In \cite{henrio:Forte2016}, we have also shown a detailed example of the construction of a complex open transition, building a deduction tree using rules \TrUn ~and \TrDeux.
-
-We have shown in \cite{henrio:Forte2016} that an open pNet
+In \cite{henrio:Forte2016}, we have  shown a detailed example of the construction of a complex open transition, building a deduction tree using rules \TrUn ~and \TrDeux.
+We have also shown in \cite{henrio:Forte2016} that an open pNet
 with finite synchronisation sets, finitely many leaves and
@@
 
-\subsection*{Example}  Figure~\ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the specification pNet given in Figure \ref{SimpleProt:Spec}. 
+\TODO{Nommer proprement chaque pnet pour pouvoir s'y referencer}
+\subsection*{Example}  Figure~\ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the specification pNet \TODO{SimpleSystem?} given in Figure \ref{SimpleProt:Spec}. 
 For later references, we give to the transitions of this (strong)
 specification automaton as $SS_i$ while transitions of the
-implementation automaton will be labelled $SI_i$. In the figure we
+implementation automaton \TODO{name} will be labelled $SI_i$. In the figure \TODO{number or figures?} we
 have annotated each global state with the set of corresponding pLTS variables.
@@
 
-    Figure \ref{SimpleProtCounter:ImplOA} shows the open automaton of the implementation $SimpleSystem$ (Figure \ref{SimpleProt:Impl}).
+    Figure \ref{SimpleProtCounter:ImplOA} shows the open automaton of the \TODO{implementation} $SimpleSystem$ (Figure \ref{SimpleProt:Impl}).
 In this drawing, we have short labels for states, representing $\ostate{s_0,m_0,r_0}$ by \texttt{000}.
@@
 \begin{example} [A weak open-transition]
-Figure \ref{WOT2} shows the construction of one of the weak transitions of the Specification OA.
+Figure \ref{WOT2} shows the construction of one of the weak transitions of the \TODO{Specification} OA.
 On the top we show the subset of the original open automaton (from Figure \ref{SimpleProtCounter:SpecOA}) considered here, and at the bottom the generated weak transition.
@@
   \begin{example}[Weak open automata]
-    Figures \ref{SimpleProtCounter:WeakSpecOA} and \ref{SimpleProtCounter:ImplWOA2} respectively show the weak automata of the simple protocol specification and implementation.
+    Figures \ref{SimpleProtCounter:WeakSpecOA} and \ref{SimpleProtCounter:ImplWOA2} respectively show the weak automata of the \TODO{simple protocol specification} and \TODO{implementation}.
 We encode weak open transitions  by $WS$ on the specification model and by $WI$ on the implementation model.
@@
 
- For readability, we do not include the full details of the Implementation weak open transitions in Figure \ref{SimpleProtCounter:ImplWOA2}, but we show some examples below and the full list is included in Appendix \ref{Appendix:FullExample}.
+ For readability, we do not include the full details of the \TODO{Implementation} weak open transitions in Figure \ref{SimpleProtCounter:ImplWOA2}, but we show some examples below and the full list is included in Appendix \ref{Appendix:FullExample}.
 First, let us point out that the weak OT loops ($WI_1$,$WI_2$ and $W_\tau$) on state ${000}$ are also present in all other states, we did not repeat them.
@@
 
-Now let us give some details about the construction of the weak automaton of the implementation pNet, obtained by application of the weak rules as explained above.
+Now let us give some details about the construction of the weak automaton of the \TODO{implementation} pNet, obtained by application of the weak rules as explained above.
 We concentrate on weak open transitions $WI_3$ and $WI_4$.
@@
 \label{subsubsection:runnig example}
-In Section~\ref{sec:weak} we have shown the full satured weak automaton for both the specification and the implementation of the simple protocol.
+In Section~\ref{sec:weak} we have shown the full saturated weak automaton for both the \TODO{specification} and the \TODO{implementation} of the simple protocol.
 We will show here how we can check if some given relation between these two automata is a weak FH-Bisimulation.
@@
 \hline
-    Spec state & Impl state & Predicate\\
+    \TODO{Spec} state & \TODO{Impl} state & Predicate\\
     \hline
@@
 
-\TODO{relire}
-pNets have through composition  the ability both to add new holes to a system and to fill holes, obtaining a system with less holes.
-They support the refinement checking at the automata level through a simulation approach, with symbolic evaluation of
+pNets support the refinement checking at the automata level through a simulation approach, with symbolic evaluation of
 the guards and transitions. 
@@
 Such a relation should be able to check the refinement between two open automata with the same level of abstraction but specified differently, for example, by duplicating states, removing transitions, reinforcing guards, modifying variables.
-But it also should  support the  comparison of automata that do not have the same number of holes.
+Additionally, composition of
+pNets gives the possibility to either add new holes to a system or  fill holes.
+A useful simulation relation  should thus support the  comparison of automata that do not have the same number of holes.
+Designing such a simulation relation is a non-trivial extension of this work that we are investigating.
 
@@
 
-The first piece of code is the textual definition of the SimpleSystemSpec
-pNet (named SimpleProtSpec2 in the code here), that was drawn in Figure \ref{SimpleProt:Impl}, page \pageref{SimpleProt:Impl}. This code should be intuitive enough to read, with the following
+The first piece of code is the textual definition of the \TODO{SimpleSystemSpec}
+pNet (named \TODO{SimpleProtSpec2} in the code here), that was drawn in Figure \ref{SimpleProt:Impl}, page \pageref{SimpleProt:Impl}. This code should be intuitive enough to read, with the following
 language conventions, that brings some user-friendly features, mapped by the editor into pure pNet constructs.
@@
 
-Next is the code for the SimpleSystem implementation pNet (named SimpleProtImpl2):
+Next is the code for the \TODO{SimpleSystem implementation} pNet (named \TODO{SimpleProtImpl2}):
 \medskip
@@
    \centerline{\includegraphics[width=10cm]{XFIG/SimpleProtImpl-WOA2}}
-   \caption{Weak Open Automaton of the implementation}
+   \caption{Weak Open Automaton of the \TODO{implementation}}
    \label{Appendix:ImplOA2}
@@
 %More tricky, they do not have the same state variables, as 202 has the variables of state $s2$, but none of these variables are used in transitions from 202.
-In this configuration we can guarantee that they are Weak bisimilar, and we have merged their (incoming and outgoing) transitions in the Figure. We denote this 
+In this configuration we can guarantee that they are Weak bisimilar, and we have merged their (incoming and outgoing) transitions in the figure. We denote this 
 equivalence class of states as $\{000,202\}$.
@@
     \bigskip
-    That makes a total of 73 WOTs  in the SimpleImpl WOA.
+    That makes a total of 73 WOTs  in the \TODO{SimpleImpl} WOA.
 
@@
 
-         Note: if we were using the alternative Weak bisim from Appendix \ref{app-WFH-equiv}, Lemma \ref{lem-rel-OT-WOT}, that is checking strong bisimulation between the corresponding 
-weak automaton, we would have a more transitions coverage to examine, as we have 4 weak transitions for $b0$ in the specification weak automaton, and 7 WOTs (including 4 
-parameterised WOTs) from 000 in the implementation automaton.
+         Note: if we were using the alternative Weak bisimulation relation from Appendix \ref{app-WFH-equiv}, Lemma \ref{lem-rel-OT-WOT}, that is checking strong bisimulation between the corresponding
+weak automaton, we would have a more transitions coverage to examine, as we have 4 weak transitions for $b0$ in the \TODO{specification} weak automaton, and 7 WOTs (including 4 
+parameterised WOTs) from 000 in the \TODO{implementation} automaton.
 
@@
 transitions (m, msg, ec) are the same, that is not correct. In the tools, this is managed by the static semantic layer; in the following example, we have renamed all conflicting 
-variables using suffix 1 for the Specification, and 2 for the Implementation.
+variables using suffix 1 for the \TODO{Specification}, and 2 for the \TODO{Implementation}.
     \end{itemize}

### 2021-10-06 2016-Weak-FH-Bisim/WeakBisim.tex
ajout related work; cond transi

@@
 
+Among the approaches for modelling open systems, where both a component and  its environment (other components) can be designed, by automata we find the theory of interface automata \cite {deAlfaro:2001} and conditional transition systems \cite{Beohar:2020}.
+Our formalism open automata is different from both, in that they are parametrised models.
+
 There is also a clear relation with the seminal works on rule formats for Structured Operational Semantics, e.g.
@@
 Then our compositionality result is more powerful than their classical results, but this is not a surprise, as we rely on a (sufficient) syntactic hypothesis on a particular system, rather than the general rules defining an operator.
-Last, we intentionaly do not accept negative premisses, that would be more diffcult to put into practice in our implementation.
+Last, we intentionally do not accept negative premisses, that would be more  to put into practice in our implementation.
 an extension could be studied in future work.
@@
 They developed the theory of symbolic transition graphs (STG), and the associated symbolic (early and late, strong and weak) bisimulations, they also study STGs with assignments as a model for message-passing processes.
-Our work extends these in several ways: first our models are compositional, and our bismulations come with effective conditions for being preserved by pNet composition (i.e.
+Our work extends these in several ways: first our models are compositional, and our bisimulations come with effective conditions for being preserved by pNet composition (i.e.
 congruent), even for the weak version.

### 2021-10-06 2016-Weak-FH-Bisim/WeakBisim.tex
meeting 1

@@
  We first define a strong bisimulation for open pNets.
- \TODO{virer cette phrase, doublon du 1er paragraph? LUDO: OK} In practice, as happens in process algebras, strong bisimulation is too strong, and
-  we define some coarser relations, taking into account
-  invisible or internal moves.
+% \TODO{virer cette phrase, doublon du 1er paragraph? LUDO: OK} In practice, as happens in process algebras, strong bisimulation is too strong, and
+%  we define some coarser relations, taking into account
+%  invisible or internal moves.
   We then define an equivalence relation similar to
@@
 
-Figure \ref{SimpleProt:Spec} (right) shows a graphical view of the pNet that specifies the system:
-the full system should be equivalent (e.g.  weakly bisimilar)
-to the two processes connected simply through a perfect medium.  
+Figure \ref{SimpleProt:Spec} (right) shows a graphical view of the pNet $\symb{SimpleProtocolSpec}$ that specifies the system.
+The pNet is made of the composition of two pNets: a $\symb{SimpleSystem}$ node, and a $\symb{PerfectBuffer}$ sub-pNet.
+The full system implementation should be equivalent (e.g.  weakly bisimilar)
+to thhis $\symb{SimpleProtocolSpec}$.  
 The pNet has a tree-like structure.
@@
 
-Figure \ref{SimpleProt:Impl} shows the pNet model of the protocol implementation.
+Figure \ref{SimpleProt:Impl} shows the pNet model of the protocol implementation, called $\symb{SimpleProtocolImpl}$ .
 When the $\symb{Medium}$ detects an error (modelled by a local $\tau$ action), it sends back a $\texttt{m-error}$ message to the $\symb{Sender}$.
@@
    \includegraphics[width=.62\textwidth]{XFIG/SimpleProt2-Spec.pdf}
-   \caption{pNet structure of the example and its specification expressed as a pNet}
+   \caption{pNet structure of the example and its specification expressed as a pNet called $\symb{SimpleProtocolSpec}$ }
    \label{SimpleProt:Spec}
@@
 
-\TODO{remove this sentence: 
-In the following, we refer to the automaton of a specification by $\symb{Spec}$ and of an implementation by $\symb{Impl}$.}
-
 \begin{figure}[t]
   \centerline{\includegraphics[width=.95\textwidth]{XFIG/SimpleProt2-pNet-tau}}
-  \caption{The $\symb{SimpleSystem}$ pNet composed with the implementation of $\symb{SimpleProtocol}$}  \label{SimpleProt:Impl}
+  \caption{The $\symb{SimpleProtocolImpl}$ pNet resulting from the composition of  the $\symb{SimpleSystem}$  and the $\symb{SimpleProtocol}$ pNets.}  \label{SimpleProt:Impl}
 \end{figure}
@@
 	Where $J'\subseteq J$ is the set of holes involved in the transition; $s, s'\in\mathcal{S}$ are states of the automaton; and $\beta_j$
-        is a transition of the hole $j$, with \hl{$\Sortop(\beta_j)\in\Sort_j$. $\alpha$}  is an action 
+        is a transition of the hole $j$, with $\Sortop(\beta_j)\in\Sort_j$. $\alpha$  is an action 
         label denoting the resulting action of this open transition.
@@
 
-\TODO{Nommer proprement chaque pnet pour pouvoir s'y referencer}
-\subsection*{Example}  Figure~\ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the specification pNet \TODO{SimpleSystem?} given in Figure \ref{SimpleProt:Spec}. 
-For later references, we give to the transitions of this (strong)
-specification automaton as $SS_i$ while transitions of the
-implementation automaton \TODO{name} will be labelled $SI_i$. In the figure \TODO{number or figures?} we
-have annotated each global state with the set of corresponding pLTS variables.
+\subsection*{Example}  Figure~\ref{SimpleProtCounter:SpecOA} shows the open automaton computed from the \symb{SimpleProtocolSpec} pNet  given in Figure \ref{SimpleProt:Spec}. 
+For later references, we name $SS_i$ the transitions of this (strong)
+specification automaton while transitions of the
+ \symb{SimpleProtocolImpl} pNet are labelled $SI_i$.
+ In the figures we
+annotate each open automaton with the set of its variables.
 
@@
 
-    Figure \ref{SimpleProtCounter:ImplOA} shows the open automaton of the \TODO{implementation} $SimpleSystem$ (Figure \ref{SimpleProt:Impl}).
+    Figure \ref{SimpleProtCounter:ImplOA} shows the open automaton of  \symb{SimpleProtocolImpl} from Figure \ref{SimpleProt:Impl}.
 In this drawing, we have short labels for states, representing $\ostate{s_0,m_0,r_0}$ by \texttt{000}.
@@
 an open transition of $Q$, and building a corresponding transition of
-$P[Q]_{j_0}$ \hl{assembling their predicates}.
+$P[Q]_{j_0}$  by assembling their elements.
 
@@
 \begin{example} [A weak open-transition]
-Figure \ref{WOT2} shows the construction of one of the weak transitions of the \TODO{Specification} OA.
+Figure \ref{WOT2} shows the construction of one of the weak transitions of the open automaton of \symb{SimpleProtocolSpec}.
 On the top we show the subset of the original open automaton (from Figure \ref{SimpleProtCounter:SpecOA}) considered here, and at the bottom the generated weak transition.
@@
   \begin{example}[Weak open automata]
-    Figures \ref{SimpleProtCounter:WeakSpecOA} and \ref{SimpleProtCounter:ImplWOA2} respectively show the weak automata of the \TODO{simple protocol specification} and \TODO{implementation}.
+    Figures \ref{SimpleProtCounter:WeakSpecOA} and \ref{SimpleProtCounter:ImplWOA2} respectively show the weak automata of \symb{SimpleProtocolSpec} and \symb{SimpleProtocolImpl}.
 We encode weak open transitions  by $WS$ on the specification model and by $WI$ on the implementation model.
@@
 
- For readability, we do not include the full details of the \TODO{Implementation} weak open transitions in Figure \ref{SimpleProtCounter:ImplWOA2}, but we show some examples below and the full list is included in Appendix \ref{Appendix:FullExample}.
-First, let us point out that the weak OT loops ($WI_1$,$WI_2$ and $W_\tau$) on state ${000}$ are also present in all other states, we did not repeat them.
-Then many WOTs are similar, and numbered accordingly as 3, 3a, 3b, 3c and 8, 8a, 8b, 8c respectively: they only differ by their respective source or target states; the "variant" WOTs appear in blue in   Figure \ref{SimpleProtCounter:ImplWOA2}.
+ For readability, we only give names to the  weak open transitions of \symb{SimpleProtocolImpl} in Figure \ref{SimpleProtCounter:ImplWOA2}; we detail some of these transitions below and the full list is included in Appendix \ref{Appendix:FullExample}.
+Let us point out that the weak OT loops ($WI_1$,$WI_2$ and $W_\tau$) on state ${000}$ are also present in all other states, we did not repeat them.
+Additionally, many WOTs are similar, and numbered accordingly as 3, 3a, 3b, 3c and 8, 8a, 8b, 8c respectively: they only differ by their respective source or target states; the "variant" WOTs appear in blue in   Figure~\ref{SimpleProtCounter:ImplWOA2}.
 \end{example}
@@
 
-Now let us give some details about the construction of the weak automaton of the \TODO{implementation} pNet, obtained by application of the weak rules as explained above.
+Now let us give some details about the construction of the weak automaton of the \symb{SimpleProtocolImpl} pNet, obtained by application of the weak rules as explained above.
 We concentrate on weak open transitions $WI_3$ and $WI_4$.
@@
 \label{subsubsection:runnig example}
-In Section~\ref{sec:weak} we have shown the full saturated weak automaton for both the \TODO{specification} and the \TODO{implementation} of the simple protocol.
+In Section~\ref{sec:weak} we have shown the full saturated weak automaton for both \symb{SimpleProtocolSpec} and \symb{SimpleProtocolImpl}.
 We will show here how we can check if some given relation between these two automata is a weak FH-Bisimulation.
@@
     \item We must take care of variable name conflicts: in our example, the variables of the 2 systems already have different names, but the action parameters occurring in the transitions (\texttt{m}, \texttt{msg}, \texttt{ec}) are the same, that is not correct.
-In the tools, this is managed by the static semantic layer; in the following example, we have renamed all conflicting variables with 1 for the Spec, and 2 for the Impl.
+In the tools, this is managed by the static semantic layer; in the  example, we rename the only conflicting variables $m$ into $m1$ for \symb{SimpleProtocolSpec}, and $m2$ for \symb{SimpleProtocolImpl}.
     \end{itemize}
@@
 
+\noindent
   \begin{tabular}{|c|c|l|}
 \hline
-    \TODO{Spec} state & \TODO{Impl} state & Predicate\\
+     \symb{SimpleProtocolSpec} states&   \symb{SimpleProtocolImpl} states& Predicate\\
     \hline

### 2021-10-06 2016-Weak-FH-Bisim/WeakBisim.tex
spec and impl in appendix

@@
 %methods of different interfaces).
-$\setminus$ is the standard subtraction operation on indexed sets: $\dom(A\setminus B)=\dom(A)\setminus B$.
+The standard subtraction operation on indexed sets is $\setminus$, with $\dom(A\setminus B)=\dom(A)\setminus B$.
 
@@
 These partial functions are sometimes called \emph{substitution functions} in the following.
- $\subst{\Post}$ is thus the operation that applies,  in a parallel manner,  the substitution defined by the partial function $\Post$.
+Thus,
+ $\subst{\Post}$ is  the operation that applies,  in a parallel manner,  the substitution defined by the partial function $\Post$.
 $\otimes$ is a composition operator on these partial functions, such that for any term $t$ we have: $t\subst{\Post\shortotimes\Post'} = (t\subst{\Post'})\subst{\Post}$.
@@
 We simply say that two sorts are compatible if they consist of the same actions with the same arity.
-In practice, it is sufficient to check the equality of the two sets of pairs $(\alpha,n)$ of the two sorts\footnote{A more complex compatibility relation could be defined, but this is out of the scope of this article.}.
+In practice, it is sufficient to check the equality of the two sets of action signatures of the two sorts\footnote{A more complex compatibility relation could be defined, but this is out of the scope of this article.}.
 \end{definition}
@@
 equivalent states can trigger transitions with identical action labels.
-Its key characteristics are 1) the introduction of predicates in the bisimulation relation: as states may contain variables, relation between states may depend on the value of the variables; 2) the bisimulation property relates elements of the open transitions and takes into account predicates over variables, actions of the holes, and state modifications.
+Its key characteristics are 1) the introduction of predicates in the bisimulation relation: the relation between states may depend on the value of the variables; 2) the bisimulation property relates elements of the open transitions and takes into account predicates over variables, actions of the holes, and state modifications.
  We name it FH-bisimulation,
@@
    \centerline{\includegraphics[width=13cm]{XFIG/SPSpecOpen}}
-   \caption{Open Automaton of  $\symb{SimpleProtocolSpec}$}
+   \caption{Open automaton for  $\symb{SimpleProtocolSpec}$}
    \label{SimpleProtCounter:SpecOA}
@@
   \centerline{\includegraphics[width=15cm]{XFIG/SPImplOpen}}
-  \caption{Open Automaton of $\symb{SimpleProtocolImpl}$}  \label{SimpleProtCounter:ImplOA}
+  \caption{Open automaton for $\symb{SimpleProtocolImpl}$}  \label{SimpleProtCounter:ImplOA}
 \end{figure}
@@
 
+ \TODO{a counter example in  CCS}
+
 \subsection{Properties of weak bisimulation for open pNets}
@@
 
+\TODO{Conclude with CCS as an example}
 \subsubsection*{Running example}
@@
 Our formalism open automata is different from both, in that they are parametrised models.
+
+\TODO{LUDO idees: \cite{Beohar:2020} conditions de transitions et bisim basees la dessus, leur bisimulation est plus logique et plus riche de ce cote, la notre plus structurelle et plus orientee composition, de facon liee ils voient l environnement comme repondant a des relaations l=ogiques avec certaines rpoprietes, on ne prend pas en compte un environnement mais on a des regles de compositions entre systemes et etablit une bisim prenant ca en compte}
 
@@
 \label{Appendix:FullExample}
+\TODO{Ludo: spec implem dans l annexe}
 
@@
 
-The first piece of code is the textual definition of the \TODO{SimpleSystemSpec}
-pNet (named \TODO{SimpleProtSpec2} in the code here), that was drawn in Figure \ref{SimpleProt:Impl}, page \pageref{SimpleProt:Impl}. This code should be intuitive enough to read, with the following
+The first piece of code is the textual definition of the $\symb{SimpleProtocolSpec}$
+pNet, that was drawn in Figure \ref{SimpleProt:Impl}, page \pageref{SimpleProt:Impl}. This code should be intuitive enough to read, with the following
 language conventions, that brings some user-friendly features, mapped by the editor into pure pNet constructs.
@@
 \begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
-SimpleProtSpec2:
+SimpleProtocolSpec:
 import "Data_Alg.algp"
-root SimpleProtSpec2
+root SimpleProtocolSpec
 const in, out:Action
@@
 
-pNet SimpleProtSpec2
+pNet SimpleProtocolSpec
 holes P,Q
@@
 
-Next is the code for the \TODO{SimpleSystem implementation} pNet (named \TODO{SimpleProtImpl2}):
+Next is the code for the \symb{SimpleProtocolImpl} pNet:
 \medskip
 \begin{lstlisting}[basicstyle=\scriptsize\ttfamily, language=java, frame=single]
-SimpleProtImpl2:
+SimpleProtocolImpl:
   import "Data_Alg.algp"
-  root SimpleProtImpl2
+  root SimpleProtocolImpl
 const in,out:Action
@@
 
-pNet SimpleProtImpl2
+pNet SimpleProtocolImpl
   holes P,Q
@@
    \centerline{\includegraphics[width=10cm]{XFIG/SimpleProtImpl-WOA2}}
-   \caption{Weak Open Automaton of the \TODO{implementation}}
+   \caption{Weak Open Automaton for \symb{SimpleProtocolImpl}}
    \label{Appendix:ImplOA2}
@@
 
-In Figure \ref{Appendix:ImplOA2} we recall the weak open automaton of our implementation pNet.
-
+In Figure \ref{Appendix:ImplOA2} we recall the weak open automaton of \symb{SimpleProtocolImpl}. 
 This drawing is based on the observation that states 202 and 000 are only linked by a "pure $\tau$" transition, and have exactly the same possible behaviours.
@@
          Note: if we were using the alternative Weak bisimulation relation from Appendix \ref{app-WFH-equiv}, Lemma \ref{lem-rel-OT-WOT}, that is checking strong bisimulation between the corresponding
-weak automaton, we would have a more transitions coverage to examine, as we have 4 weak transitions for $b0$ in the \TODO{specification} weak automaton, and 7 WOTs (including 4 
-parameterised WOTs) from 000 in the \TODO{implementation} automaton.
+weak automaton, we would have a more transitions coverage to examine, as we have 4 weak transitions for $b0$ in the \symb{SimpleProtocolSpec} weak automaton, and 7 WOTs (including 4 
+parameterised WOTs) from 000 in the \symb{SimpleProtocolImpl} automaton.
 
@@
   \begin{itemize}
-    \item Both pNets trivialy verify the ``non-observability''
+    \item Both pNets trivially verify the ``non-observability''
       condition: the only vectors having $\tau$ as an action of a
@@
     \item We must take care of variable name conflicts: in our example, the variables of the 2 systems already have different names, but the action parameters occurring in the 
-transitions (m, msg, ec) are the same, that is not correct. In the tools, this is managed by the static semantic layer; in the following example, we have renamed all conflicting 
-variables using suffix 1 for the \TODO{Specification}, and 2 for the \TODO{Implementation}.
+transitions (m, msg, ec) are the same, that is not correct.
+Recall that we disambiguate the reference to the variable $m$ into $m1$ for \symb{SimpleProtocolSpec} and $m2$ for \symb{SimpleProtocolImpl}.
     \end{itemize}

### 2021-10-06 2016-Weak-FH-Bisim/2021-09-letter2Reviewers.tex

@@
 \section*{Annex 1: response to first reviewers' comments}
+- The definition of pNets is cumbersome.
+I understand that this work extends prior work where the model has been motivated already, but I have my reservations on the utility of the formalisms.
+I found the running example (although useful) to be hard to understand.
+It would perhaps be useful to provide anecdotal evidence showing that comparable formalisms cannot handle certain features of the example (which would justify the complexity of the model used).
+
+- I was left unconvinced that using open automata as an intermediary structure to define the bisimualtion relations is the best approach to develop this material.
+The authors should give more convincing argument that such definitions could not be adequately defined directly on pNets (an already complex framework).
+It left me wondering:
+1) How do you validate the translation of pNets to Open Automata?  Shouldn't there be some result that states that the translation is semantic preserving?    
+2) Why not work directly in terms of Open Automata (and forget all about pNets)?
+A prima facie, they appear to be of a comparable complexity to pNets (if not simpler).
+There are few people who would be interested in using a framework that relies on the second rule in Def 9 as a modelling language...
+
+- The definition of bisimulation is slightly non-standard (eg Def 7).
+For instance, why does the transfer property require a "set" of matching transitions?
+Normally, the existence of one suffices.
+Moreover, given that a set is required, shouldn't there be an additional requirement that the matching set is necessarily non-empty?
+
+- In general, weak bisimulation is *not* a congruence for all types of interacting contexts.  For instance, in the case of CCS, the classsical counter example is that whereas 
+tau.a.0  \\bisim  a.0
+we do *not* have
+tau.a.0 + b.0 \\bisim  a.0 + b.0 
+Given the generality of the pNets framework I found the claim stated in Theorem 7 to be suspicious (and hard to ascertain).
+The authors should perhaps provide more intuition why this is the case for their framework.
 
 \section*{Annex 2: response to second reviewers' comments}
+DETAILED COMMENTS
+
+P1 Abstract L10 *… that includes parameters, and …* parameters for what? Please elaborate more on this in the introduction.
+
+P2 L24 *… provides a cleaner version…* I am afraid such a sentence does not add any value if there is no explanation discussing it in detail somewhere later in the paper.
+
+P3 L-11 What is an action algebra? I believe it is an undefined term in the paper.
+
+P4 L-6 *We distinguish two kinds….* please rewrite this sentence
+
+P4 L1 We additionally *impose*
+
+P4 L6 *negociation* typo
+
+P4 L20 A minor point: Technically, $a^{i\in 3}$ is not allowed by your syntax since indices need to also appear as a subscript.
+
+P4 L22 I am afraid we do not use abusive vocabulary in mathematics, rather we only abuse notation. Please rewrite.
+
+P4 L26 *\\uplus is the disjoint union of sets* Please rewrite this sentence; it is considered to be a bad practice to start the sentence with a symbol (cf.
+Donald Knuth on mathematical writing available from $https://jmlr.csail.mit.edu/reviewing-papers/knuth_mathematical_writing.pdf$).
+
+P4 L-9 *We denote y <- e a substitution* What do you mean by this? Do you mean that y<-e is a partial function from the set of variables to terms that is only defined for the variable y as the term e?
+
+P4 L-9 *The application of a substitution…* Its strange to denote an application of a substitution without any denotation for its argument.
+
+P4 L-7 The notion of substitutions on indexed sets is more subtle; they may not be a function unlike a substitution in the traditional setting. For e.g., $x_1 <-e, x_2 <-e’ with x_1 = x_2$.
+
+P4 L-6 *\\otimes is the composition operator…* Is this operation totally defined? This even makes it necessary that substitutions are defined properly.
+
+P4 L-2 Missing comma
+
+P5 Def 1 Is vars(s) defined earlier?
+
+P5 Def 2 How is the symbol $l$ quantified in the clause pertaining to synchronisation vectors.
+
+P6 Def 3 In the first clause defining Sort, the notation *?x <- x* is not defined since, technically, a substitution substitutes a variable not a term like ?x.
+
+P6 Def 3 In the third item, *indexes* should be *indices*
+
+P6 L-15 It would be nice to have a sentence motivating synchronisation vectors that they are essentially transitions; here the example from 2.3 was helpful.
+
+P6 Def 4 When is a pNet of the right sort?
+
+P9 Def 5 Here, is $Sort_j$ again a set of parameterised actions?
+
+P9 Def 5 L6 *all variables in the different terms $\beta_j$ and $\alpha$* What do you mean by this phrase?
+
+P9 Def 5 L7 By *assignments* do you mean indexed substitutions?
+
+P9 Def 6 L-4 Please explain *simple logic* and *paper rules* in more detail?
+
+P9 Def 6 L-2 open with capital O
+
+P9 Def 6 L8 *We take in this article …* Doesn’t add anything and it isn’t clear what the writer is trying to convey here?
+I guess that the intent is to stay that the set of transition is closed under the implication given below in Page 9.
+
+Also, it would be good to add some accompanying texts that explain this implication. My understanding is that this implication says that the set of open transitions is closed under the
+refinement of predicates, which is a strong assumption from the modelling point of view. This is because modeller is forced to add new behaviour which (s)he is not interested to capture.
+Lastly, I was anticipating a more formal way to derive transitions of an open automaton just like how transitions are derived by a witnessing proof in the context of transition system specifications.
+For latter, a reference is as follows:
+J.F. Groote. Transition system specifications with negative premises. TCS 118, 1993 $https://www.sciencedirect.com/science/article/pii/0304397593901116$
+Also, I believe that the induced transitions in T are all meaningful (in the sense of Glabbeek, see below) because there are no negative transitions in the premise of an open transition.
+R.J. van Glabbeek. The meaning of negative premises in transition system specifications II. JLAP, 2004 $https://www.sciencedirect.com/science/article/pii/S1567832604000281$
+Such a discussion with a possible related work is missing and should be provided at least in a separate remark.
+
+P10 Def 7 L-6 Typo *!J* should be just *J*
+
+P10 Def 7 It was frustrating to not find out what is the type of an FH-bisimulation R, which I think is necessary if you want to compute such an R.
+Firstly, it should be mentioned that $Pred_{s,t}$ is some predicate over $V_1 \cup V_2$.
+Second, please give the formal type of conditional relation R before defining the transfer property of an FH-bisimulation.
+Here, by a conditional relation R on the sets X and Y I mean a function of type $X \times Y ---> L$, where L is some lattice modelling the values that the relation can take.
+For instance, traditional relation on X and Y can be seen as a function $X \times Y ---> 2$, where 2={0,1} is the obvious Boolean algebra of two point set; so $x R y \iff R(x,y)=1$.
+Similarly, in your case, the lattice L should be the Boolean algebra P(Pred), where P(X) is the powerset of X, for any set X.
+This raises the issue whether FH-bisimulation is an instance of conditional bisimulation (when the lattice L is P(Pred) ) as defined in the following paper:
+H.Beohar, B. König, S. Küpper,  A. Silva. Conditional transition systems with upgrades. $https://www.sciencedirect.com/science/article/abs/pii/S0167642319301169$
+
+P11 L1 What is X in the open transition $OT_x^{x\in X}$?
+
+P11 L2 Typo: jx as the subscript of \\beta. You could use $\beta_{j_x}$?
+
+P11 L-8 What do you mean by a finite predicate?
+
+P12 L6 Could you expand on what is bisimulation theory for open pNets?
+
+P13 Def 9 Please exemplify *I\_1 for the others*?
+
+P13 Def 9 In the first line of the premise of Tr2, shouldn’t the occurrences of $\alpha’ in SV_k just be \alpha$?
+
+P13 Def 9 Tr2 by *$fresh(\alpha’_m,\alpha’,\beta_j,\alpha)$* should be understand that the variables occurring in $\alpha’_m,\alpha’, \beta_j$ (for all j), and $\alpha$ are fresh?
+
+P16 L-4 You claim Theorem 5 is quite useful in practice; however, I wonder here about FH-simulation.
+First, whether a similar result holds for simulation?
+Second, FH-simulaton would be more relevant if we
+disallow that the set of transitions in an open automaton are closed under the refinement of predicates (Def. 6).
+
+P17 Def 11 Isn’t (1) a special case of (2)?
+
+P18 Def 12 Other than the symbol used for weak transition, is there any semantic difference in Def 12 between a weak open transition and an open transition defined earlier?
+
+P22 L-1 Shouldn’t Pred be $Pred_{s,t}$? Again, please give the type of this conditional relation
+
+P28 L2 *principle* --> *relations*
 

### 2021-10-06 2016-Weak-FH-Bisim/WeakBisim.tex
impl et spec en annexe
cond transition ref

@@
 In most of the transitions, you can observe that data is propagated between the successive pLTS variables (holding the message, and the error counter value).
-On the right of the figure, you have a loop of $\tau$ actions ($\texttt{SI}_4$, $\texttt{SI}_5$ and $\texttt{SI}_6$)  showing the handling of errors and corresponding increments of the error counter.
+On the right of the figure, there is a loop of $\tau$ actions ($\texttt{SI}_4$, $\texttt{SI}_5$ and $\texttt{SI}_6$)  showing the handling of errors and the incrementation of the error counter.
 
@@
 
-We start with decomposition: from one open transition of $P[Q]_{j_0}$, we exhibit 
+We start with a decomposition property: from one open transition of $P[Q]_{j_0}$, we exhibit 
 corresponding behaviours of $P$ and $Q$, and determine the relation between their 
-predicates:
+predicates.
 \begin{lemma}[Open transition decomposition\label{lem-decompose}] Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$}.
@@
 As  our symbolic operational semantics provides an open automaton, we can apply the notion of
-	strong (symbolic) bisimulation on automata to open pNets:
+	strong (symbolic) bisimulation on automata to open pNets.
 \begin{definition}[FH-bisimulation for open pNets]\label{def:bisim-pnets}
@@
 
-Among the approaches for modelling open systems, where both a component and  its environment (other components) can be designed, by automata we find the theory of interface automata \cite {deAlfaro:2001} and conditional transition systems \cite{Beohar:2020}.
-Our formalism open automata is different from both, in that they are parametrised models.
-
-\TODO{LUDO idees: \cite{Beohar:2020} conditions de transitions et bisim basees la dessus, leur bisimulation est plus logique et plus riche de ce cote, la notre plus structurelle et plus orientee composition, de facon liee ils voient l environnement comme repondant a des relaations l=ogiques avec certaines rpoprietes, on ne prend pas en compte un environnement mais on a des regles de compositions entre systemes et etablit une bisim prenant ca en compte}
+Among the approaches for modelling open systems, one can cite  \cite{Beohar:2020} that uses transition conditions depending on an external environment, and introduce bisimulation relations based on this approach.
+The approach of  \cite{Beohar:2020} is
+  highly based on logics and their bisimulation theory richer in this aspect, while our theory is highly structural and focuses on relation between structure and equivalence.
+Also, we see composition as a structural operation putting systems together, and do not focus on the modelisation of an unknown outside world.
+Overall we believe that the two approaches are complementary but checking the compatibility of the two different bisimulation theories is not  trivial.
+
+%where both a component and  its environment (other components) can be designed, by automata we find the theory of interface automata \cite {deAlfaro:2001} and conditional transition systems \cite{Beohar:2020}.
+Our formalism open automata is different from
 
@@
     \bigskip
-    That makes a total of 73 WOTs  in the \TODO{SimpleImpl} WOA.
+    That makes a total of 73 WOTs  in the open automaton for \symb{SimpleProtocolImpl}.
 
@@
 \bigskip
-  \begin{tabular}{|c|c|l|}
+\noindent  \begin{tabular}{|c|c|l|}
 \hline
-    \TODO{Spec} state & \TODO{Impl} state & Predicate\\
+    \symb{SimpleProtocolSpec} states & \symb{SimpleProtocolImpl} states & Predicate\\
     \hline

### 2021-10-07 2016-Weak-FH-Bisim/WeakBisim.tex
improved todos
changt otimes + typos mineurs

@@
 \newcommand{\shortotimes}{\!\otimes\!}
+\newcommand{\shortodot}{\!\odot\!}
 \usepackage{macrospNets}
@@
 We develop here a semantics for a model of interacting processes with parameters and holes. 
-Our approach is originaly inspired from Structured Operational Semantics with conditional premisses as in \cite{GROOTE1993263,VANGLABBEEK2004229}.
-But we aim at a more constructive and implementable appraoch to compute the semantics (intuitively transitions including first order predicates) and to 
+Our approach is originally inspired from Structured Operational Semantics with conditional premisses as in \cite{GROOTE1993263,VANGLABBEEK2004229}.
+But we aim at a more constructive and implementable approach to compute the semantics (intuitively transitions including first order predicates) and to 
 check equivalences for these open systems.
@@
  $\subst{\Post}$ is  the operation that applies,  in a parallel manner,  the substitution defined by the partial function $\Post$.
-$\otimes$ is a composition operator on these partial functions, such that for any term $t$ we have: $t\subst{\Post\shortotimes\Post'} = (t\subst{\Post'})\subst{\Post}$.
+$\odot$ is a composition operator on these partial functions, such that for any term $t$ we have: $t\subst{\Post\shortodot\Post'} = (t\subst{\Post'})\subst{\Post}$.
 This property must also be valid when the substitution does not operate on all variables.
@@
 
-\[(x_{k}\gets e_{k})^{k\in K}\shortotimes (x'_{k'}\gets e'_{k'})^{k'\in K'} =  
+\[(x_{k}\gets e_{k})^{k\in K}\shortodot (x'_{k'}\gets e'_{k'})^{k'\in K'} =  
 (x_{k}\gets e_{k}\subst{(x'_{k'}\gets e'_{k'})^{k'\in K'}})^{k\in K} \cup (x'_{k'}\gets e'_{k'})^{k'\in K''}\]
@@
 \begin{definition}[pNets]\label{def-pnets}
-A pNet $\pNet$ is a hierarchical structure where leaves are pLTSs and holes:\\
+A pNet $\pNet$ is a hierarchical structure where leaves are pLTSs and holes\\
 $\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in 
 K}\myrangle$
-where
+where:
 \begin{itemize}
@@
 It consists of three nodes: two holes $P$ and $Q$ and one sub-pNet, denoted {\it PerfectBuffer}.
-Nodes of the tree are synchronized using four synchronization vectors, that  express the possible synchronizations between the parameterised actions of a subset of the nodes.
-For instance, in the vector $< \texttt{p-send(m)},\texttt{in(m)},\_> \rightarrow \texttt{\nounderline{in(m)}}$ only $P$ and {\it PerfectBuffer} nodes are involved in the synchronization.
-The synchronization between these processes occurs when  process $P$  performs $\texttt{p-send(m)}$  action sending a message, and  the {\it PerfectBuffer} accepts the message through an $\texttt{in(m)}$ action  at the same time; the result that will be returned at upper level is the action  $\texttt{\nounderline{in(m)}}$.
+Nodes of the tree are synchronised using four synchronisation vectors, that  express the possible synchronisations between the parameterised actions of a subset of the nodes.
+For instance, in the vector $< \texttt{p-send(m)},\texttt{in(m)},\_> \rightarrow \texttt{\nounderline{in(m)}}$ only $P$ and {\it PerfectBuffer} nodes are involved in the synchronisation.
+The synchronisation between these processes occurs when  process $P$  performs $\texttt{p-send(m)}$  action sending a message, and  the {\it PerfectBuffer} accepts the message through an $\texttt{in(m)}$ action  at the same time; the result that will be returned at upper level is the action  $\texttt{\nounderline{in(m)}}$.
 
@@
          {
-           \set{\beta}\subst{\Post}, \Pred\,'\subst{\Post}\land\Pred,\Post\shortotimes\Post\,'}
+           \set{\beta}\subst{\Post}, \Pred\,'\subst{\Post}\land\Pred,\Post\shortodot\Post\,'}
          {\raisemath{-2pt}{t \OTarrow {\alpha\subst{\Post}} {t'}}{}}
@@
 
-The parametric nature of the automata entails a second original aspect of FH-bisimulation : the nature of the bisimulation relation itself.
+The parametric nature of the automata entails a second original aspect of FH-bisimulation: the nature of the bisimulation relation itself.
  A classical relation between states can be seen as a function mapping pairs of state to a boolean value (true if the states are related, false if they are not).
@@
 \\
-\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land \Pred_3\subst{\Post_2\shortotimes\Post_1}
+\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land \Pred_3\subst{\Post_2\shortodot\Post_1}
 \\
-\set{\gamma}=\set{\gamma_1}\dotcup \set{\gamma_2}\subst{\Post_1}\dotcup\set{\gamma_3}\subst{\Post_2\shortotimes \Post_1}\\
+\set{\gamma}=\set{\gamma_1}\dotcup \set{\gamma_2}\subst{\Post_1}\dotcup\set{\gamma_3}\subst{\Post_2\shortodot \Post_1}\\
 \alpha'=\alpha\subst{\Post_1}
@@
 		\Pred,
-				\Post_3\shortotimes\Post_2\shortotimes\Post_1} 
+				\Post_3\shortodot\Post_2\shortodot\Post_1} 
          {s \OTWeakarrow {\alpha'} s'} \in\WT
@@
 Their values thus depend on the initial state but also on the effect (as a substitution function $\Post_1$) of the first weak open transition.
-In the same manner, $\Pred_3$ must be applied the substitution defined by the composition $\Post_2\shortotimes\Post_1$.
+In the same manner, $\Pred_3$ must be applied the substitution defined by the composition $\Post_2\shortodot\Post_1$.
 Similarly, effects on variables must be applied to obtain the global effect of the composed weak open transition, it must also be applied to observable actions of the holes, and to the global action of the weak open transition.
@@
 			() }
-         {\texttt{b1} \OTWeakarrow \tau \texttt{b1}}$. Then Rule \WTTrois~ produces  $\openrule
+         {\texttt{b1} \OTWeakarrow \tau \texttt{b1}}$. The result will be:   $\openrule
          {\{\}, True,
@@
 
-Then the effect of one single $100 \xrightarrow{OT_4} 210 \xrightarrow{OT_5} 220 \xrightarrow{OT_6} 100$ loop is\footnote{when showing  the result of $Posts$ composition, we will omit the identity substitution functions introduced by the $\shortotimes$ definition in page \pageref{def:substitutions}}:
-\[post_{456} = post_6 \shortotimes\ post_5 \shortotimes\ post_4
+Then the effect of one single $100 \xrightarrow{OT_4} 210 \xrightarrow{OT_5} 220 \xrightarrow{OT_6} 100$ loop is\footnote{when showing  the result of $Posts$ composition, we will omit the identity substitution functions introduced by the $\shortodot$ definition in page \pageref{def:substitutions}}:
+\[post_{456} = post_6 \shortodot\ post_5 \shortodot\ post_4
 = (\texttt{s\_ec}\gets \texttt{s\_ec}+1)\]
@@
 So if we denote ${post_{456*}}$ any iteration of this loop, we get ${post_{456*}} = (\texttt{s\_ec}\gets \texttt{s\_ec}+n)$ for any $n\ge 0$, and the \Post~ of the weak OT  $WI_{3}$ is:\\
- $Post_3 = post_{456*}\shortotimes\ post_3 = (\texttt{s\_msg}\gets m, \texttt{s\_ec}\gets n), \forall n\ge 0$ and \Post~ of  $WI_{3a}$  is:\\ $post_4\shortotimes {post_{456*}}\shortotimes\ post_3 = (\texttt{m\_msg}\gets m, \texttt{m\_ec}\gets n), \forall n\ge 0$.
+ $Post_3 = post_{456*}\shortodot\ post_3 = (\texttt{s\_msg}\gets m, \texttt{s\_ec}\gets n), \forall n\ge 0$ and \Post~ of  $WI_{3a}$  is:\\ $post_4\shortodot {post_{456*}}\shortodot\ post_3 = (\texttt{m\_msg}\gets m, \texttt{m\_ec}\gets n), \forall n\ge 0$.
 \medskip
@@
 \begin{array}{l@{}l}
-Post_{6a}&= post_{4}\shortotimes\ post_{456*}\shortotimes\ post_{6}\\ 
+Post_{6a}&= post_{4}\shortodot\ post_{456*}\shortodot\ post_{6}\\ 
 &=  (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec})\,
-\shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+n) 
-\shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+1) \\
+\shortodot (\texttt{s\_ec}\gets \texttt{s\_ec}+n) 
+\shortodot (\texttt{s\_ec}\gets \texttt{s\_ec}+1) \\
 &= (\texttt{m\_msg}\!\gets \texttt{s\_msg}, \texttt{m\_ec}\!\gets \texttt{s\_ec}+1\!+\!n, \texttt{s\_ec}\!\gets \texttt{s\_ec}+1\!+\!n)
@@
 \end{mathpar}
- there exist weak open transitions $\symb{WOT}_x^{\;x\in X} \subseteq \WT_2$:
+ there exists an indexed set of weak open transitions $\symb{WOT}_x^{\;x\in X} \subseteq \WT_2$:
  \begin{mathpar}
@@
 Two pNets are weak FH-bisimilar if there exists a relation between their associated 
-automata that is a Weak FH-bisimulation and their initial states are in the relation, i.e. 
+automata that is a weak FH-bisimulation and their initial states are in the relation, i.e. 
 the predicate associated to the relation between the initial states is \True.
@@
 
-Our first important result is that Weak FH-bisimilarity is an equivalence in the same way as strong FH-bisimilarity:
+Our first important result is that weak FH-bisimilarity is an equivalence in the same way as strong FH-bisimilarity:
 
@@
 
-In which $fv_{OT}$ denotes the set of free variables of all expressions in $OT$.
+where $fv_{OT}$ denotes the set of free variables of all expressions in $OT$.
 \subsection{Weak bisimulation for open pNets}
@@
 
-With this definition, it is easy to check that the open automaton that gives the semantics of such an open pNet cannot observe silent actions in the sense of Definition~\ref{def:Non-ObsTau}:
+With this definition, it is easy to check that the open automaton that gives the semantics of such an open pNet cannot observe silent actions in the sense of Definition~\ref{def:Non-ObsTau}.
 
@@
 
-%where both a component and  its environment (other components) can be designed, by automata we find the theory of interface automata \cite {deAlfaro:2001} and conditional transition systems \cite{Beohar:2020}.
-Our formalism open automata is different from
+%where both a component and  its environment (other components) can be designed, by automata we find the theory of interface automata \cite {deAlfaro:2001} and conditional
 
@@
 Open pNets are pNets with holes; they are adapted to represent processes parameterised by the behaviour of other processes, like composition operators or interaction 
-protocols that synchronize the actions of processes that can be plugged afterwards. Open
+protocols that synchronise the actions of processes that can be plugged afterwards. Open
 pNets are hierarchical composition of automata with holes and parameters. We
@@
 We  define a quantified composition operator for effects, i.e. $\Post$ elements of the open transitions.
-We use ${\displaystyle \bigotimes_{i=n}^{0} \Post_i}$ to denote  $\Post_n\otimes .. \otimes \Post_0$. By convention ${\displaystyle \bigotimes_{i=-1}^{0} \Post_i}$ is the identity.
+We use ${\displaystyle \bigodot_{i=n}^{0} \Post_i}$ to denote  $\Post_n\otimes .. \otimes \Post_0$. By convention ${\displaystyle \bigodot_{i=-1}^{0} \Post_i}$ is the identity.
 
@@
 $
-\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=n}^{0}\Post_{1j}}}\\
+\alpha'=\alpha\displaystyle{\subst{\bigodot_{j=n}^{0}\Post_{1j}}}\\
 s=s_{10} \wedge s_{1(n+1)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
 \displaystyle{
-\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup}\\
-{}~\qquad \displaystyle{\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }}
+\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigodot_{j=n}^{0}\Post_{1j}}} \dotcup}\\
+{}~\qquad \displaystyle{\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}} }}
 \\
-\Pred=\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=n}^{0}\Post_{1j}}\land\\ 
-{}~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}}\Big)\\
-\Post=\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}
+\Pred=\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigodot_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j=n}^{0}\Post_{1j}}\land\\ 
+{}~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}}\Big)\\
+\Post=\bigodot_{j=m}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}
 $
@@
 s''=s_{10} &\wedge s_{1(n+2)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
-\alpha'=&\alpha\displaystyle{\subst{\bigotimes_{j=n+1}^{1}\!\!\Post_{1j}}}\\
-\set{\gamma}=&\mybigdotcup_{i=1}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup\\
-& \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }\\
-\Pred=&\bigwedge_{i=1}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{1}\Post_{1j}}\land\\ 
-&\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}}\Big)\\
-\Post=&\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{1}\Post_{1j}
+\alpha'=&\alpha\displaystyle{\subst{\bigodot_{j=n+1}^{1}\!\!\Post_{1j}}}\\
+\set{\gamma}=&\mybigdotcup_{i=1}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigodot_{j=n+1}^{1}\Post_{1j}}} \dotcup\\
+& \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}} }\\
+\Pred=&\bigwedge_{i=1}^{n+1}\Pred_{1i}\subst{\bigodot_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j={n+1}}^{1}\Post_{1j}}\land\\ 
+&\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j={n+1}}^{1}\Post_{1j}}\Big)\\
+\Post=&\bigodot_{j=m}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j={n+1}}^{1}\Post_{1j}
 \end{align*}
@@
 \Pred\,''\!=\!\Pred_{10}\land\Pred\subst{\Post_{10}}\\\\%\land (\Pred_3\subst{\Post_2})\subst{\Post_{10}}
-\Post\,''=\Id(s'')\shortotimes\Post\shortotimes\Post_{10} \\ \alpha''=\alpha'\subst{\Post_{10}}
+\Post\,''=\Id(s'')\shortodot\Post\shortodot\Post_{10} \\ \alpha''=\alpha'\subst{\Post_{10}}
 }
@@
 s_{10}=s_{10} &\wedge s_{1(n+2)}=s_{2} \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
-\alpha''=&\alpha\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}\subst{\Post_{10}} = \alpha\subst{\bigotimes_{j=n+1}^{0}\Post_{1j}}\\
-\set{\gamma''}=&\mybigdotcup_{i=0}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n+1}^{1}\Post_{1j}}} \dotcup\\
-&\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }
+\alpha''=&\alpha\subst{\bigodot_{j=n+1}^{1}\Post_{1j}}\subst{\Post_{10}} = \alpha\subst{\bigodot_{j=n+1}^{0}\Post_{1j}}\\
+\set{\gamma''}=&\mybigdotcup_{i=0}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigodot_{j=n+1}^{1}\Post_{1j}}} \dotcup\\
+&\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}} }
 \\
-\Pred=&\bigwedge_{i=0}^{n+1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j={n+1}}^{0}\Post_{1j}}\land\\ 
-&\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{0}\Post_{1j}}\Big)
+\Pred=&\bigwedge_{i=0}^{n+1}\Pred_{1i}\subst{\bigodot_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j={n+1}}^{0}\Post_{1j}}\land\\ 
+&\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j={n+1}}^{0}\Post_{1j}}\Big)
 \\
-\Post=&\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j={n+1}}^{0}\Post_{1j}
+\Post=&\bigodot_{j=m}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j={n+1}}^{0}\Post_{1j}
 \end{align*}
@@
 		\Pred,
-				\Post_3\shortotimes{\Post_2}\shortotimes{\Post_1} }
+				\Post_3\shortodot{\Post_2}\shortodot{\Post_1} }
          {s \OTWeakarrow {\alpha'} s'''} \in\WT
@@
 s=s_{10} \wedge s_{1{(n_1+1)}}\!=s',\quad
-\displaystyle{\set{\gamma_1}= \mybigdotcup_{i=0}^{n_1} \vis{\set{\beta_{1 i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1 j} } }} \\
-\Pred_1\!=\!\bigwedge_{i=0}^{n_1}(\Pred_{1i} \subst{\bigotimes_{j=i-1}^{0}\Post_{i j}} ), \quad \Post_1= \bigotimes_{i=n_1}^{0} \subst{\Post_{1i}} 
+\displaystyle{\set{\gamma_1}= \mybigdotcup_{i=0}^{n_1} \vis{\set{\beta_{1 i}}\subst{\bigodot_{j=i-1}^{0} \Post_{1 j} } }} \\
+\Pred_1\!=\!\bigwedge_{i=0}^{n_1}(\Pred_{1i} \subst{\bigodot_{j=i-1}^{0}\Post_{i j}} ), \quad \Post_1= \bigodot_{i=n_1}^{0} \subst{\Post_{1i}} 
 $
@@
 
-\displaystyle{\set{\gamma_3}= \mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{3 i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{3 j} } }}
+\displaystyle{\set{\gamma_3}= \mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{3 i}}\subst{\bigodot_{j=i-1}^{0} \Post_{3 j} } }}
 
@@
 
-\Pred_3\!=\!\bigwedge_{i=0}^{m_1}(\Pred_{3i} \subst{\bigotimes_{j=i-1}^{0}\Post_{3 j}} )
+\Pred_3\!=\!\bigwedge_{i=0}^{m_1}(\Pred_{3i} \subst{\bigodot_{j=i-1}^{0}\Post_{3 j}} )
 
@@
 
- \Post_3= \bigotimes_{i=m_1}^{0} \subst{\Post_{3i}} 
+ \Post_3= \bigodot_{i=m_1}^{0} \subst{\Post_{3i}} 
 \end{mathpar}
@@
 s'=s_{20} &\wedge s_{2(n_2+1)}=s_2 \wedge  s_2' = s_{20}' \wedge s_{2(m_2+1)}'=s''\\
-\alpha''=&\alpha'\subst{\bigotimes_{j=n_2}^{0}\Post_{2j}}\\
-\set{\gamma_2}=&\mybigdotcup_{i=0}^{n_2} \vis{\set{\beta_{2i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{2 j} } }  \dotcup  \vis{\set{\beta'}\subst{\bigotimes_{j=n_2}^{0}\Post_{2j}}} \dotcup\\
+\alpha''=&\alpha'\subst{\bigodot_{j=n_2}^{0}\Post_{2j}}\\
+\set{\gamma_2}=&\mybigdotcup_{i=0}^{n_2} \vis{\set{\beta_{2i}}\subst{\bigodot_{j=i-1}^{0} \Post_{2 j} } }  \dotcup  \vis{\set{\beta'}\subst{\bigodot_{j=n_2}^{0}\Post_{2j}}} \dotcup\\
 &
- \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{2i}} \subst{\bigotimes_{j=i-1}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j=n_2}^{0}\Post_{2j}}}
+ \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{2i}} \subst{\bigodot_{j=i-1}^{0}\Post\,'_{2j}\shortodot\Post\,'\shortodot\bigodot_{j=n_2}^{0}\Post_{2j}}}
 \\
-\Pred_2=&\bigwedge_{i=0}^{n_2}\Pred_{2i}\subst{\bigotimes_{j=i-1}^{0}\Post_{2j}}\land\Pred\,' \subst{\bigotimes_{j={n_2}}^{0}\Post_{2j}}\land\\ 
-&\Big(\bigwedge_{i=0}^{m_2}\Pred\,'_{2i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}}\Big)\\
-\Post_2=&\bigotimes_{j=m_2}^{0}\Post\,'_{2j}\shortotimes\Post\,'\shortotimes\bigotimes_{j={n_2}}^{0}\Post_{2j}
+\Pred_2=&\bigwedge_{i=0}^{n_2}\Pred_{2i}\subst{\bigodot_{j=i-1}^{0}\Post_{2j}}\land\Pred\,' \subst{\bigodot_{j={n_2}}^{0}\Post_{2j}}\land\\ 
+&\Big(\bigwedge_{i=0}^{m_2}\Pred\,'_{2i}\subst{\bigodot_{j=i-1}^{0}\Post\,'_{2j}\shortodot\Post\,'\shortodot\bigodot_{j={n_2}}^{0}\Post_{2j}}\Big)\\
+\Post_2=&\bigodot_{j=m_2}^{0}\Post\,'_{2j}\shortodot\Post\,'\shortodot\bigodot_{j={n_2}}^{0}\Post_{2j}
 \end{align*}
@@
 s\!=\!s_{40}& ~\wedge~s_{4(n_1+n_2+1)}\!=s_2 ~\wedge~s_2' = s_{50} ~\wedge~ s_{5(m_1+m_2+1)}\!=\!s'\\
-\alpha''=&\alpha\subst{\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}\\
-\set{\gamma}=&\mybigdotcup_{i=0}^{n_1+n_2} \vis{\set{\beta_{4i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{4 j} } }  \dotcup  \vis{\set{\beta'}\subst{\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}}\dotcup \\
-&\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta_{5i}}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{5i}\shortotimes\Post\,'\shortotimes\!\!\bigotimes_{j=n_1+n_2}^{0}\!\!\!\Post_{4i}} }\\
+\alpha''=&\alpha\subst{\!\!\bigodot_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}\\
+\set{\gamma}=&\mybigdotcup_{i=0}^{n_1+n_2} \vis{\set{\beta_{4i}}\subst{\bigodot_{j=i-1}^{0} \Post_{4 j} } }  \dotcup  \vis{\set{\beta'}\subst{\!\!\bigodot_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}}\dotcup \\
+&\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta_{5i}}\subst{\bigodot_{j=i-1}^{0}\Post\,'_{5i}\shortodot\Post\,'\shortodot\!\!\bigodot_{j=n_1+n_2}^{0}\!\!\!\Post_{4i}} }\\
 \Pred=&
-\bigwedge_{i=0}^{n_1+n_2}\!\!\Pred_{4i}\subst{\bigotimes_{j=i-1}^{0}\Post_{4j}}\land\Pred\,' \subst{\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\!\Post_{4j}}\land\\ 
-&\quad\bigwedge_{i=0}^{m_1+m_2}\Pred_{5i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{5j}\shortotimes\Post\,'\shortotimes\!\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\!\Post_{4j}}\\
-\Post=&\bigotimes_{j=m_1+m_2}^{0}\!\!\!\Post_{5j}\shortotimes\Post\,'\shortotimes\!\!\bigotimes_{j={n_1+n_2}}^{0}\!\!\Post_{4j}
+\bigwedge_{i=0}^{n_1+n_2}\!\!\Pred_{4i}\subst{\bigodot_{j=i-1}^{0}\Post_{4j}}\land\Pred\,' \subst{\!\!\bigodot_{j={n_1+n_2}}^{0}\!\!\!\Post_{4j}}\land\\ 
+&\quad\bigwedge_{i=0}^{m_1+m_2}\Pred_{5i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post_{5j}\shortodot\Post\,'\shortodot\!\!\!\bigodot_{j={n_1+n_2}}^{0}\!\!\!\Post_{4j}}\\
+\Post=&\bigodot_{j=m_1+m_2}^{0}\!\!\!\Post_{5j}\shortodot\Post\,'\shortodot\!\!\bigodot_{j={n_1+n_2}}^{0}\!\!\Post_{4j}
 \end{align*}
@@
 where
+
 \begin{align*}
 s=s_{10} &\wedge s_{1(n+1)}=s_{20} \wedge s_{21} = s_{30} \wedge s_{3(m+1)}=s'\\
-\alpha=&\alpha'\subst{\bigotimes_{j=n}^{0}\Post_{1j}}\\
-\gamma_j^{j\in J'}=&\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=n}^{0}\Post_{1j}}} \dotcup\\
-&\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}} }
+\alpha=&\alpha'\subst{\bigodot_{j=n}^{0}\Post_{1j}}\\
+\gamma_j^{j\in J'}=&\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigodot_{j=n}^{0}\Post_{1j}}} \dotcup\\
+&\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}} }
 \\
-\Pred_{OT}=&\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=n}^{0}\Post_{1j}}\land\\ 
-&\qquad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}}\Big)\\
-\Post_{OT}=&\bigotimes_{j=m}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=n}^{0}\Post_{1j}
+\Pred_{OT}=&\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigodot_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j=n}^{0}\Post_{1j}}\land\\ 
+&\qquad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}}\Big)\\
+\Post_{OT}=&\bigodot_{j=m}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}
 \end{align*}
@@
 \\ 
-\set{\gamma'}=\gamma_{j a}^{j\in J_{a}} \dotcup \gamma_{jb}^{j\in J_{b}} \subst{\Post_{OT_a}} \dotcup\gamma_{jc}^{j\in J_{c}} \subst{\Post_{OT_{ b}}\shortotimes\Post_{OT_a}}\\
-\Pred=\Pred_{OT_a}\land\Pred_{OT_{b}}\subst{\Post_{OT_a}}\land \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}\\
-\Post= \Post_{OT_{c}} \shortotimes \Post_{OT_{b}}\shortotimes\Post_{OT_{a}}\quad \alpha''=\alpha_{2}\subst{\Post_{OT_a}}\\
+\set{\gamma'}=\gamma_{j a}^{j\in J_{a}} \dotcup \gamma_{jb}^{j\in J_{b}} \subst{\Post_{OT_a}} \dotcup\gamma_{jc}^{j\in J_{c}} \subst{\Post_{OT_{ b}}\shortodot\Post_{OT_a}}\\
+\Pred=\Pred_{OT_a}\land\Pred_{OT_{b}}\subst{\Post_{OT_a}}\land \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortodot\Post_{OT_a}}\\
+\Post= \Post_{OT_{c}} \shortodot \Post_{OT_{b}}\shortodot\Post_{OT_{a}}\quad \alpha''=\alpha_{2}\subst{\Post_{OT_a}}\\
 }
@@
 We have:\\
-$\Pred_{OT}= \Pred_1 \wedge \Pred_2\subst{\Post_1} \wedge \Pred_3\subst{\Post_2\shortotimes\Post_1}$\\
-$\Post_{OT}=\Post_3\shortotimes \Post_2\shortotimes\Post_1$\\
+$\Pred_{OT}= \Pred_1 \wedge \Pred_2\subst{\Post_1} \wedge \Pred_3\subst{\Post_2\shortodot\Post_1}$\\
+$\Post_{OT}=\Post_3\shortodot \Post_2\shortodot\Post_1$\\
 Moreover, we have the following  statement:\\
@@
 \vis{\beta_{1j}}\!\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-\vis{\beta_{2j}}\!=\!\gamma_{jb}\subst{\Post_1\uplus\Post_{OT_a}}   \land\Pred_{OT_a} \land \\ \Pred_{OT_{b}} \subst{\Post_1\uplus\Post_{OT_a}} \land  (\alpha'\!=\!\alpha_{2 b}) \subst{\Post_1\uplus\Post_{OT_a}} \land \\ \Pred_{s_{21},b}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})
+\vis{\beta_{2j}}\!=\!\gamma_{jb}\subst{\Post_1\uplus\Post_{OT_a}}   \land\Pred_{OT_a} \land \\ \Pred_{OT_{b}} \subst{\Post_1\uplus\Post_{OT_a}} \land  (\alpha'\!=\!\alpha_{2 b}) \subst{\Post_1\uplus\Post_{OT_a}} \land \\ \Pred_{s_{21},b}\subst{\Post_2\shortodot\Post_1\uplus \Post_{OT_{b}}\shortodot \Post_{OT_a}})
 \end{multline*}
@@
 \vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-\vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jb} \subst{\Post_{OT_a}}  \land\Pred_{OT_a} \land \\ \Pred_{OT_{b}} \subst{\Post_{OT_a}} \land \alpha'\subst{\Post_1}=\alpha_{2 b} \subst{\Post_{OT_a}} \land\\ \Pred_{s_{21},b}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})\end{multline*}
-Finally, the conjunction with the term $\Pred_3\subst{\Post_2\shortotimes\Post_1}$ of the both sides of the implication and rewriting, we get:
-\begin{multline*}(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}\implies \\
+\vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jb} \subst{\Post_{OT_a}}  \land\Pred_{OT_a} \land \\ \Pred_{OT_{b}} \subst{\Post_{OT_a}} \land \alpha'\subst{\Post_1}=\alpha_{2 b} \subst{\Post_{OT_a}} \land\\ \Pred_{s_{21},b}\subst{\Post_2\shortodot\Post_1\uplus \Post_{OT_{b}}\shortodot \Post_{OT_a}})\end{multline*}
+Finally, the conjunction with the term $\Pred_3\subst{\Post_2\shortodot\Post_1}$ of the both sides of the implication and rewriting, we get:
+\begin{multline*}(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortodot\Post_1}\implies \\
 \displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}} 
 (\forall j\in J_a.\vis{\beta^1_j}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-\vis{\beta_{2j}}\subst{\Post_1}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}\land \Pred_{OT_a}\land\\\Pred_{OT_{b}}\subst{\Post_{OT_a}} \land  \alpha'\subst{\Post_1}= \alpha_{2 b} \subst{\Post_{OT_a}} \land (\Pred_{s_{21},v_b} \land  \Pred_3)\\ \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{b}}\shortotimes\Post_{OT_a}})\end{multline*}
-Again note that because of the domain  of the substitution function is independent from some predicates and expressions, we removed $\Post_1$ and  we  added the term $\Post_{OT_{b}}\shortotimes\,\Post_{OT_a}$ in the substitution of the right side of the implication.\\
+\vis{\beta_{2j}}\subst{\Post_1}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}\land \Pred_{OT_a}\land\\\Pred_{OT_{b}}\subst{\Post_{OT_a}} \land  \alpha'\subst{\Post_1}= \alpha_{2 b} \subst{\Post_{OT_a}} \land (\Pred_{s_{21},v_b} \land  \Pred_3)\\ \subst{\Post_2\shortodot \Post_1\uplus \Post_{OT_{b}}\shortodot\Post_{OT_a}})\end{multline*}
+Again note that because of the domain  of the substitution function is independent from some predicates and expressions, we removed $\Post_1$ and  we  added the term $\Post_{OT_{b}}\shortodot\,\Post_{OT_a}$ in the substitution of the right side of the implication.\\
 Finally, by replacing the predicate $(\Pred_{s_{21},b} \land  \Pred_3)$
 by the conclusion of the  implication given in case 3, we get:
-\begin{multline*}\Pred_{s,t} \land \underbrace{\Pred_1\land \Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortotimes\Post_1}}_{\Pred_{OT}}\implies\\
+\begin{multline*}\Pred_{s,t} \land \underbrace{\Pred_1\land \Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortodot\Post_1}}_{\Pred_{OT}}\implies\\
  {\bigvee_{a\in A}}\, {\bigvee_{b\in B}}\, {\bigvee_{c\in C}} 
 (\forall\! j\in\! J_a.\vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \!\in\! J_{b}.\vis{\beta_{2j}\subst{\Post_{OT_a}}}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}  \land \\
- \forall j\!\in\! J_{c}. \vis{\beta_{3j} \subst{\Post_2\,\shortotimes\,\Post_1}} \!=\!\gamma_{jc} \subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}  \land\\
+ \forall j\!\in\! J_{c}. \vis{\beta_{3j} \subst{\Post_2\,\shortodot\,\Post_1}} \!=\!\gamma_{jc} \subst{\Post_{OT_{b}}\shortodot\Post_{OT_a}}  \land\\
    \underbrace{\Pred_{OT_a}\land\Pred_{OT_{b}} \subst{\Post_{OT_a}} \land 
-  \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}}_{\Pred} \land  \underbrace{\alpha'\subst{\Post_1}}_{\alpha}=\underbrace{\alpha_{2 b} \subst{\Post_{OT_a}}}_{\alpha''} \\\land \Pred_{s_{31},c}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{c}}\shortotimes \Post_{OT_{b}}\shortotimes\Post_{OT_a}}_{\Post}})
+  \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortodot\Post_{OT_a}}}_{\Pred} \land  \underbrace{\alpha'\subst{\Post_1}}_{\alpha}=\underbrace{\alpha_{2 b} \subst{\Post_{OT_a}}}_{\alpha''} \\\land \Pred_{s_{31},c}  \subst{\underbrace{\Post_3\shortodot\Post_2\shortodot\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{c}}\shortodot \Post_{OT_{b}}\shortodot\Post_{OT_a}}_{\Post}})
 \end{multline*}
@@
 \begin{multline*}\forall j\in J_a\uplus J_b\uplus J_c.
-\vis{\beta_{1j}}\dotcup \vis{\beta_{2j}\subst{\Post_{OT_a}}}\dotcup \vis{\beta_{3j} \subst{\Post_2\shortotimes\Post_1}}=\\ ~\hspace{5.5cm} \gamma_{j a} \dotcup \gamma_{jb} \subst{\Post_{OT_a}}  \dotcup \gamma_{jc} \subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}
+\vis{\beta_{1j}}\dotcup \vis{\beta_{2j}\subst{\Post_{OT_a}}}\dotcup \vis{\beta_{3j} \subst{\Post_2\shortodot\Post_1}}=\\ ~\hspace{5.5cm} \gamma_{j a} \dotcup \gamma_{jb} \subst{\Post_{OT_a}}  \dotcup \gamma_{jc} \subst{\Post_{OT_{b}}\shortodot\Post_{OT_a}}
 \end{multline*}
@@
 \text{, }
- \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigotimes_{i=p-1}^{0}\Post_i}, \\
+ \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigodot_{i=p-1}^{0}\Post_i}, \\
 {~\hspace{2cm}}\Pred \iff \Pred\,'
-		\land \!\!\bigwedge_{p=0}^n(\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i} = \beta_p\land \Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i} ),
+		\land \!\!\bigwedge_{p=0}^n(\alpha_p\subst{\bigodot_{i=p-1}^{0}\Post_i} = \beta_p\land \Pred_p\subst{\bigodot_{i=p-1}^{0}\Post_i} ),
 \\
-{~\hspace{2cm}}\Post=\Post\,' \uplus \bigotimes_{p=n}^0
+{~\hspace{2cm}}\Post=\Post\,' \uplus \bigodot_{p=n}^0
 		\Post_p,   \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\
@@
 \forall l\in L.\,&s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l\\
-\alpha=&\alpha'{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}}\\
-\gamma_j^{j\in J}=&\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\! \Post_{1j}}}\dotcup\  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup  
-{\mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }}
+\alpha=&\alpha'{\subst{\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}}\\
+\gamma_j^{j\in J}=&\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{0}\!\! \Post_{1j}}}\dotcup\  \vis{\set{\beta_2}\subst{\bigodot_{j=m_1}^{0}\Post_{1j}}} \dotcup  
+{\mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}} }}
 \\
-\Pred=&\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\land
-\bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
-\Post=&\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}
+\Pred=&\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}\land
+\bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}\\
+\Post=&\bigodot_{j=m_2}^{0}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}
 \end{align*}}
@@
 where
-$\alpha''=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}}$\\
+$\alpha''=\alpha'\displaystyle{\subst{\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}}}$\\
 On the other hand, we have:
-$\alpha=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}}\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,''_{1j}}}=\alpha''\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,''_{1j}}}$.\\
-As $\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,''_{1j}}}$ has no effect on variables of $P$ and thus on variables of $\alpha''$, so we have $\alpha=\alpha''$.
+$\alpha=\alpha'\displaystyle{\subst{\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}}}\displaystyle{\subst{\bigodot_{j=m_1}^{0}\!\!\Post\,''_{1j}}}=\alpha''\displaystyle{\subst{\bigodot_{j=m_1}^{0}\!\!\Post\,''_{1j}}}$.\\
+As $\displaystyle{\subst{\bigodot_{j=m_1}^{0}\!\!\Post\,''_{1j}}}$ has no effect on variables of $P$ and thus on variables of $\alpha''$, so we have $\alpha=\alpha''$.
 \\
@@
 \forall l\in L.\,&s_l=s_{0l} \wedge s_{(m_1+1)l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)l}=s'_l\\
-{(\gamma_j')}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}=&\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}}} \dotcup\\
+{(\gamma_j')}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}=&\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{0}\!\!\Post\,'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigodot_{j=m_1}^{0}\Post\,'_{1j}}}} \dotcup\\
 & \mybigdotcup_{i=0}^{m_2}
-\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}} }
+\vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\!\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}} }
 \\
-\Pred\,'=&\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}\land\\ 
-&\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}\\
-\Post'=&\bigotimes_{j=m_2}^{0}\!\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}
+\Pred\,'=&\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}}\land\\ 
+&\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}}\\
+\Post'=&\bigodot_{j=m_2}^{0}\!\!\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}
 \end{align*}}
@@
 %Concerning $\gamma'_{j_0}$ we have:
-%\[\gamma'_{j_0}=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{{\alpha_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}} \dotcup\\
+%\[\gamma'_{j_0}=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{{\alpha_{1i}}\subst{\bigodot_{j=i-1}^{0}\!\!\Post'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigodot_{j=m_1}^{0}\Post'_{1j}}}} \dotcup\\
 %~~\qquad \mybigdotcup_{i=0}^{m_2}
-%\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}} }\]
+%\vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigodot_{j=m_1}^{0}\!\!\Post'_{1j}} }\]
 
@@
 $\begin{array}{l}\displaystyle{
-\Pred_\beta=\bigwedge_{p=0}^{m_1}(\beta_{1pj_0}=\alpha_{1p})\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}} \wedge (\beta_{2j_0}=\alpha_{20})\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}} \wedge \\\qquad\qquad
+\Pred_\beta=\bigwedge_{p=0}^{m_1}(\beta_{1pj_0}=\alpha_{1p})\subst{\bigodot_{j=p-1}^{0}\!\!\Post_{1j}} \wedge (\beta_{2j_0}=\alpha_{20})\subst{\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}} \wedge \\\qquad\qquad
 \displaystyle{
 \bigwedge_{p=0}^{m_2}(\beta_{3pj_0}=\alpha_{3p})
-\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}}
+\subst{\bigodot_{j=p-1}^{0}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}}
 \end{array}$
@@
 \begin{split}
-(\alpha_{1p}=\beta_{1pj_0})\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}&\iff
-\alpha_{1p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,''_{1j}}
-= \beta_{1 p j_0}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,'_{1j}} \\
-&\iff\alpha'_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post\,''_{j}}= \beta_{1 p j_0}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,'_{1j}} 
+(\alpha_{1p}=\beta_{1pj_0})\subst{\bigodot_{j=p-1}^{0}\!\!\Post_{1j}}&\iff
+\alpha_{1p}\subst{\bigodot_{j=p-1}^{0}\!\!\Post\,''_{1j}}
+= \beta_{1 p j_0}\subst{\bigodot_{j=p-1}^{0}\!\!\Post\,'_{1j}} \\
+&\iff\alpha'_k\subst{\bigodot_{j=k-1}^{0}\!\!\Post\,''_{j}}= \beta_{1 p j_0}\subst{\bigodot_{j=p-1}^{0}\!\!\Post\,'_{1j}} 
 \end{split}
@@
 \Pred_\beta \iff \gamma_{j_0}=
-\vis{[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post\,''_{j}}|p\in[0..n_1+n_2+2]]}
+\vis{[\alpha'_{p}\subst{\bigodot_{j=p-1}^{0}\!\!\Post\,''_{j}}|p\in[0..n_1+n_2+2]]}
 \end{equation}
@@
 \forall l \in L_Q. &v_{kl}=v_{(n'_{k})l} \wedge v_{kl}'=v_{(n'_k)l}\\
-\alpha_k=&\alpha'_{n_k}{\subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}}\\
-{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=&{\mybigdotcup_{i=n'_{k}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=i-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}} \dotcup\\
+\alpha_k=&\alpha'_{n_k}{\subst{\bigodot_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}}\\
+{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=&{\mybigdotcup_{i=n'_{k}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigodot_{l=i-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigodot_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}} \dotcup\\
 &\mybigdotcup_{i=n_k+1}^{n'_{k+1}-1}
-\vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}} \subst{\bigotimes_{l=i-1}^{n_k\!+\!1}\!\Post\,''_{l}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}} }\\
-\Pred_k=&\bigwedge_{i=n'_{k}}^{n_k\!-\!1}\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\Pred\,''_{n_k} \subst{\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\\ 
-&\bigwedge_{i=n_k+1}^{n'_{k+1}-1}\!\!\!\Pred\,''_{i}\subst{\bigotimes_{j=i-1}^{n'_{k}}\!\!\!\Post\,''_{j}\shortotimes\Post\,''_{n_k}\shortotimes\!\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{j}}
+\vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}} \subst{\bigodot_{l=i-1}^{n_k\!+\!1}\!\Post\,''_{l}\shortodot\Post\,''_{n_k}\shortodot\!\!\bigodot_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}} }\\
+\Pred_k=&\bigwedge_{i=n'_{k}}^{n_k\!-\!1}\!\!\Pred\,''_{i}\subst{\bigodot_{j=i-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\Pred\,''_{n_k} \subst{\bigodot_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}\land\\ 
+&\bigwedge_{i=n_k+1}^{n'_{k+1}-1}\!\!\!\Pred\,''_{i}\subst{\bigodot_{j=i-1}^{n'_{k}}\!\!\!\Post\,''_{j}\shortodot\Post\,''_{n_k}\shortodot\!\!\bigodot_{j=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{j}}
 \\
-\Post_k= &\bigotimes_{j=n'_{k+1}-1}^{n'_{k}}\!\!\Post\,''_{j}
+\Post_k= &\bigodot_{j=n'_{k+1}-1}^{n'_{k}}\!\!\Post\,''_{j}
 \end{align*}
@@
 
-\noindent By definition of $\Post_k$, we have $\displaystyle{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post\,''_{j} = \bigotimes_{j=k-1}^{0}\!\!\Post_{j}}$.
+\noindent By definition of $\Post_k$, we have $\displaystyle{\bigodot_{j=n'_{k}-1}^{0}\!\!\Post\,''_{j} = \bigodot_{j=k-1}^{0}\!\!\Post_{j}}$.
 %In this case, the number of weak open transitions
@@
 Consequently,  we have:
-\[\alpha'_{n_k}{\subst{\!\bigotimes_{j=n_k-1}^{0}\!\!\!\Post\,''_{j}}} =
-\alpha'_{n_k}\displaystyle{\subst{\!\bigotimes_{j=n_k-1}^{n'_{k}}\!\!\!\Post''_{j}\otimes\!\!\!\bigotimes_{j=n'_{k}-1}^{0}\!\!\!\Post\,''_{j}}} = \alpha_k\displaystyle{\subst{\!\bigotimes_{j=n'_{k}-1}^{0}\!\!\!\Post\,''_{j}}} =
-\alpha_k\displaystyle{\subst{\!\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}}\]
+\[\alpha'_{n_k}{\subst{\!\bigodot_{j=n_k-1}^{0}\!\!\!\Post\,''_{j}}} =
+\alpha'_{n_k}\displaystyle{\subst{\!\bigodot_{j=n_k-1}^{n'_{k}}\!\!\!\Post''_{j}\otimes\!\!\!\bigodot_{j=n'_{k}-1}^{0}\!\!\!\Post\,''_{j}}} = \alpha_k\displaystyle{\subst{\!\bigodot_{j=n'_{k}-1}^{0}\!\!\!\Post\,''_{j}}} =
+\alpha_k\displaystyle{\subst{\!\bigodot_{j=k-1}^{0}\!\!\Post_{j}}}\]
 From equation~\ref{eqproofbeta}, we obtain the following equation (we recall that the actions $\alpha_k$ are the actions $\alpha'_{p}$ that are observable): 
@@
 \mybigdotcup_{p=0}^{p=n_1+n_2+2}
-\vis{\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}}\\
+\vis{\alpha'_{p}\subst{\bigodot_{j=p-1}^{0}\!\!\Post_{j}}}\\
 %&\iff&\gamma_{j_0}=
 %\mybigdotcup_{p=0}^{p=n_1+n_2+2}
-%\vis{\alpha_{p}\subst{\bigotimes_{j=p-1}^{n'_p}\!\!\Post_{j}}\subst{\bigotimes_{j=n'_p-1}^{0}\!\!\Post_{j}}}\\
-%\vis{[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n_1+n_2+2]]}\\
+%\vis{\alpha_{p}\subst{\bigodot_{j=p-1}^{n'_p}\!\!\Post_{j}}\subst{\bigodot_{j=n'_p-1}^{0}\!\!\Post_{j}}}\\
+%\vis{[\alpha_{p}\subst{\bigodot_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n_1+n_2+2]]}\\
 %&\iff& \gamma_{j_0}=
-%\vis{[\alpha'_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[1..n]]}\\
+%\vis{[\alpha'_{p}\subst{\bigodot_{j=p-1}^{0}\!\!\Post_{j}}|p\in[1..n]]}\\
 &\iff& \gamma_{j_0}=
-[\alpha_{p}\subst{\bigotimes_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n]]
+[\alpha_{p}\subst{\bigodot_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n]]
 \end{eqnarray*}
@@
 \[  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) \qquad\text{trivial}\]
-\[ \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigotimes_{i=p-1}^{0}\Post_i)}\]
+\[ \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigodot_{i=p-1}^{0}\Post_i)}\]
 Indeed we have:
@@
 \begin{split}
-\gamma_j^{j\in J}=&\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!
-\Post_{1j}}}\dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup\\& \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }\\
+\gamma_j^{j\in J}=&\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{0}\!\!
+\Post_{1j}}}\dotcup  \vis{\set{\beta_2}\subst{\bigodot_{j=m_1}^{0}\Post_{1j}}} \dotcup\\& \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}} }\\
 \end{split}\end{equation*}
@@
 \begin{split}
-\gamma_j^{j\in J\cap \Holes(Q)}&=\mybigdotcup_{i=0}^{m_1} \vis{\set{(\beta_{1i}')}\subst{\bigotimes_{j=i-1}^{0}\!\!
-\Post''_{1j}}}\dotcup  \vis{\set{\beta'_2}\subst{\bigotimes_{j=m_1}^{0}\Post''_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post''_{3j}\shortotimes\Post''_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post''_{1j}} }\\
-&=\mybigdotcup_{k=0}^n \left( \mybigdotcup_{i=n'_k}^{n'_{k+1}-1}\vis{\beta_{ij}^{j\in J\cap \Holes(Q)}\subst{\bigotimes_{j=i-1}^{n'_k}\!\!\Post''_{j}\bigotimes_{j=n'_k-1}^{0}\!\!\Post''_{j}}}\right)\\
-&=\mybigdotcup_{k=0}^n \left( \gamma_{kj}^{j\in J\cap \Holes(Q)}\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{k}}\right)
+\gamma_j^{j\in J\cap \Holes(Q)}&=\mybigdotcup_{i=0}^{m_1} \vis{\set{(\beta_{1i}')}\subst{\bigodot_{j=i-1}^{0}\!\!
+\Post''_{1j}}}\dotcup  \vis{\set{\beta'_2}\subst{\bigodot_{j=m_1}^{0}\Post''_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{3i}} \subst{\bigodot_{j=i-1}^{0}\!\Post''_{3j}\shortodot\Post''_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post''_{1j}} }\\
+&=\mybigdotcup_{k=0}^n \left( \mybigdotcup_{i=n'_k}^{n'_{k+1}-1}\vis{\beta_{ij}^{j\in J\cap \Holes(Q)}\subst{\bigodot_{j=i-1}^{n'_k}\!\!\Post''_{j}\bigodot_{j=n'_k-1}^{0}\!\!\Post''_{j}}}\right)\\
+&=\mybigdotcup_{k=0}^n \left( \gamma_{kj}^{j\in J\cap \Holes(Q)}\subst{\bigodot_{j=k-1}^{0}\!\!\Post_{k}}\right)
 \end{split}\end{equation*}
@@
 \[\Pred = \displaystyle{\Pred\,'
-		\land \!\!\bigwedge_{p=0}^n\Big((\alpha_p\subst{\bigotimes_{i=p-1}^{0}\Post_i}) = \beta_p\land (\Pred_p\subst{\bigotimes_{i=p-1}^{0}\Post_i}) \Big)}\]
+		\land \!\!\bigwedge_{p=0}^n\Big((\alpha_p\subst{\bigodot_{i=p-1}^{0}\Post_i}) = \beta_p\land (\Pred_p\subst{\bigodot_{i=p-1}^{0}\Post_i}) \Big)}\]
 Indeed,
@@
 \begin{align*}
-\Pred&\iff\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\land
-\bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
+\Pred&\iff\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}\land
+\bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}\\
 &\iff\bigwedge_{i=0}^{m_1}\left(\Pred\,'_{1i}
-		\land {\Pred\,''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}\right)\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}} \\
+		\land {\Pred\,''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}\right)\subst{\bigodot_{j=i-1}^{0}\!\!\Post_{1j}} \\
 &\qquad\land\left(\Pred\,'_{2}
-		\land {\Pred\,''_{2}}\land \alpha_{20}=\beta_{2j_0}\right)\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
+		\land {\Pred\,''_{2}}\land \alpha_{20}=\beta_{2j_0}\right)\subst{\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}\\
 &\qquad\land\bigwedge_{i=0}^{m_2} \left(\Pred\,'_{3i}
-		\land {\Pred\,''_{3i}}\land \alpha_{3i}=\beta_{3ij_0}\right) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\displaybreak[0]\\
-&\iff\bigwedge_{i=0}^{m_1}\left((\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{1j}})
-		\land ({\Pred\,''_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,''_{1j}})\land (\alpha_{1i}=\beta_{1ij_0})\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\right) \\
-&\qquad\land \left(\Pred\,'_{2}\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}
-		\land {\Pred\,''_{2}} \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \land (\alpha_{20}=\beta_{2j_0})\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} \right) \\
-&\qquad\land\bigwedge_{i=0}^{m_2} \Bigg(\Pred\,'_{3i} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} 
-		\land {\Pred\,''_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}  \\
-		 & \qquad \land (\alpha_{3i}=\beta_{3ij_0}) \subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\Bigg)  \\
-&\iff \Pred\,'\land\bigwedge_{k=0}^n\Pred_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}\land\Pred_\beta
-\\&\iff \Pred\,'\land\bigwedge_{k=0}^n\Pred_k\subst{\bigotimes_{j=k-1}^{0}\!\!\Post_{j}}\land
-(\gamma_{j_0}=[\alpha_{i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{j}}|i\in[0..n]])
+		\land {\Pred\,''_{3i}}\land \alpha_{3i}=\beta_{3ij_0}\right) \subst{\bigodot_{j=i-1}^{0}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}\displaybreak[0]\\
+&\iff\bigwedge_{i=0}^{m_1}\left((\Pred\,'_{1i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post\,'_{1j}})
+		\land ({\Pred\,''_{1i}}\subst{\bigodot_{j=i-1}^{0}\!\!\Post\,''_{1j}})\land (\alpha_{1i}=\beta_{1ij_0})\subst{\bigodot_{j=i-1}^{0}\!\!\Post_{1j}}\right) \\
+&\qquad\land \left(\Pred\,'_{2}\subst{\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}
+		\land {\Pred\,''_{2}} \subst{\bigodot_{j=m_1}^{0}\!\!\Post_{1j}} \land (\alpha_{20}=\beta_{2j_0})\subst{\bigodot_{j=m_1}^{0}\!\!\Post_{1j}} \right) \\
+&\qquad\land\bigwedge_{i=0}^{m_2} \Bigg(\Pred\,'_{3i} \subst{\bigodot_{j=i-1}^{0}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}} 
+		\land {\Pred\,''_{3i}} \subst{\bigodot_{j=i-1}^{0}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}  \\
+		 & \qquad \land (\alpha_{3i}=\beta_{3ij_0}) \subst{\bigodot_{j=i-1}^{0}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}\Bigg)  \\
+&\iff \Pred\,'\land\bigwedge_{k=0}^n\Pred_k\subst{\bigodot_{j=k-1}^{0}\!\!\Post_{j}}\land\Pred_\beta
+\\&\iff \Pred\,'\land\bigwedge_{k=0}^n\Pred_k\subst{\bigodot_{j=k-1}^{0}\!\!\Post_{j}}\land
+(\gamma_{j_0}=[\alpha_{i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post_{j}}|i\in[0..n]])
 \end{align*}
@@
 Finally we have~~
-$\Post=\displaystyle{\Post\,' \uplus \bigotimes_{p=n}^0
+$\Post=\displaystyle{\Post\,' \uplus \bigodot_{p=n}^0
 		\Post_p}$\quad
@@
 {\small \begin{align*}
-\Post&=\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}\\
-&=\bigotimes_{j=m_2}^{0}\!\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j} \uplus \bigotimes_{j=m_2}^{0}\!\!\Post\,''_{3j}\shortotimes\Post\,''_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,''_{1j}\\
-&=\Post\,' \uplus \bigotimes_{j=n'_{n+1}-1}^{0}\!\!\Post\,''_{j}
+\Post&=\bigodot_{j=m_2}^{0}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}\\
+&=\bigodot_{j=m_2}^{0}\!\!\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j} \uplus \bigodot_{j=m_2}^{0}\!\!\Post\,''_{3j}\shortodot\Post\,''_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post\,''_{1j}\\
+&=\Post\,' \uplus \bigodot_{j=n'_{n+1}-1}^{0}\!\!\Post\,''_{j}
 \end{align*}}
-Which concludes because we have we have $\displaystyle{\bigotimes_{j=n'_{k}-1}^{0}\!\!\Post\,''_{j} = \bigotimes_{j=k-1}^{0}\!\!\Post_{j}}$.
+Which concludes because we have we have $\displaystyle{\bigodot_{j=n'_{k}-1}^{0}\!\!\Post\,''_{j} = \bigodot_{j=k-1}^{0}\!\!\Post_{j}}$.
 %
@@
 %%$\set{\gamma}= \displaystyle{\mybigdotcup_{p=0}^{n}
-%%\vis{\set{\beta_{p}}}\subst{\bigotimes_{p=n}^{0} \Post_{p}}}$\\
+%%\vis{\set{\beta_{p}}}\subst{\bigodot_{p=n}^{0} \Post_{p}}}$\\
 %Furthermore, still by hypothesis we have:\\
-%$\Pred=\displaystyle{\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }\land \\
-%~\qquad \quad \bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}$\\
+%$\Pred=\displaystyle{\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j=m_1}^{0}\!\!\Post_{1j}} }\land \\
+%~\qquad \quad \bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}$\\
 %By replacing $\Pred_{1i}$,  $\Pred_2$, and $\Pred_{3i}$ by their equivalent formula obtained from cases 1, 2 and 3 we have:\\
 %$\Pred =\displaystyle{\bigwedge_{i=0}^{m_1}({\Pred'_{1i}}
-%		\land {\Pred''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}) \bigotimes_{j=i-1}^{0}\subst{\Post_{1j}}\land}\\
-%~~\qquad\qquad({\Pred'_2}\land {\Pred''_2}\land \alpha_2=\beta_{2j_0})	\bigotimes_{i=m_1}^{0}\subst{\Post_{1i}}\land\\
+%		\land {\Pred''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}) \bigodot_{j=i-1}^{0}\subst{\Post_{1j}}\land}\\
+%~~\qquad\qquad({\Pred'_2}\land {\Pred''_2}\land \alpha_2=\beta_{2j_0})	\bigodot_{i=m_1}^{0}\subst{\Post_{1i}}\land\\
 %~~\qquad\qquad\bigwedge_{i=0}^{m_2} ({\Pred'_{3i}}\land {\Pred''_{3i}}\land \alpha_{3i}=\beta_{3ij_0})
-%\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}$\\
+%\subst{\bigodot_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}$\\
 %By distribution of the substitution operation over the logical operator we reformulate as:\\
 %$\Pred= \displaystyle{\big(\bigwedge_{i=0}^{m_1}
-%{\Pred'_{1i}}\bigotimes_{j=i-1}^{0}\subst{{\Post'_{1j}}}\big)
-%\land{\Pred'_2}\bigotimes_{i=m_1}^{0}\subst{{\Post'_{1i}}}\land} \\
-%~~\qquad\qquad\bigwedge_{i=0}^{m_2}{\Pred'_{3i}}\bigotimes_{j=i-1}^{0}\subst{{\Post'_{3j}}}\subst{{\Post'_2}}\bigotimes_{j=m_1}^{0}\subst{{\Post'_{1j}}} \land\\	
-%~\qquad\qquad\bigwedge_{i=0}^{m_1}({\Pred''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}) \bigotimes_{j=i-1}^{0}\subst{\Post_{1j}}\land({\Pred''_2}\land \alpha_2=\beta_{2j_0})	\bigotimes_{i=m_1}^{0}\subst{\Post_{1i}}\land\\
-%~\qquad\qquad\bigwedge_{i=0}^{m_2} ({\Pred''_{3i}}\land \alpha_{3i}=\beta_{3ij_0})\bigotimes_{j=i-1}^{0}\subst{\Post_{3j}}\subst{\Post_2}  \bigotimes_{i=m_1}^{0}\subst{\Post_{1i}}
+%{\Pred'_{1i}}\bigodot_{j=i-1}^{0}\subst{{\Post'_{1j}}}\big)
+%\land{\Pred'_2}\bigodot_{i=m_1}^{0}\subst{{\Post'_{1i}}}\land} \\
+%~~\qquad\qquad\bigwedge_{i=0}^{m_2}{\Pred'_{3i}}\bigodot_{j=i-1}^{0}\subst{{\Post'_{3j}}}\subst{{\Post'_2}}\bigodot_{j=m_1}^{0}\subst{{\Post'_{1j}}} \land\\	
+%~\qquad\qquad\bigwedge_{i=0}^{m_1}({\Pred''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}) \bigodot_{j=i-1}^{0}\subst{\Post_{1j}}\land({\Pred''_2}\land \alpha_2=\beta_{2j_0})	\bigodot_{i=m_1}^{0}\subst{\Post_{1i}}\land\\
+%~\qquad\qquad\bigwedge_{i=0}^{m_2} ({\Pred''_{3i}}\land \alpha_{3i}=\beta_{3ij_0})\bigodot_{j=i-1}^{0}\subst{\Post_{3j}}\subst{\Post_2}  \bigodot_{i=m_1}^{0}\subst{\Post_{1i}}
 %$\\		
 %Thus, we can write the formula as follows:\\
-%$\Pred= \Pred\,' \wedge \displaystyle{\bigwedge_{p=0}^{n}}((\alpha_p= \beta_{pj_0}\land \Pred_p)\bigotimes_{i=p-1}^{0}\Post_i)$\\
+%$\Pred= \Pred\,' \wedge \displaystyle{\bigwedge_{p=0}^{n}}((\alpha_p= \beta_{pj_0}\land \Pred_p)\bigodot_{i=p-1}^{0}\Post_i)$\\
 %We proceed the same way with the postcondition,  we have:\\
-%$\Post=\displaystyle{\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}$\\
+%$\Post=\displaystyle{\bigodot_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}$\\
 %By replacing ${\Post_{1i}}$,  $\Post_2$, and ${\Post_{3i}}$ their values obtained from the cases 1, 2, and 3, and because the ${\Post'_i}$ and ${\Post''_i}$ are independent (the ${\Post'_i}$ concern the leaves of $P$ while the ${\Post''_i}$ concern the leaves of $Q$), we obtain:\\
-%$\Post= \displaystyle{\bigotimes_{i=m_2}^{0}\subst{{\Post'_{3i}}\uplus 
+%$\Post= \displaystyle{\bigodot_{i=m_2}^{0}\subst{{\Post'_{3i}}\uplus 
 %		{\Post''_{3i}}} \subst{{\Post'_2}\uplus 
-%		{\Post''_2}} \bigotimes_{j=m_1}^{0}\subst{ {\Post'_{1i}}\uplus 
+%		{\Post''_2}} \bigodot_{j=m_1}^{0}\subst{ {\Post'_{1i}}\uplus 
 %		{\Post''_{1i}}}}\\
-%~~\qquad= \bigotimes_{i=m_2}^{0}{\Post'_{3i}}\subst{{\Post'_2}}\bigotimes_{j=m_1}^{0}\subst{{\Post'_{1j}}} \uplus \bigotimes_{i=m_2}^{0}{\Post''_{3i}}\subst{{\Post''_2}}\bigotimes_{j=m_1}^{0}\subst{{\Post''_{1j}}} \\
-%~~\qquad= \Post' \uplus \bigotimes_{j=n}^{0} \Post_j $\\
+%~~\qquad= \bigodot_{i=m_2}^{0}{\Post'_{3i}}\subst{{\Post'_2}}\bigodot_{j=m_1}^{0}\subst{{\Post'_{1j}}} \uplus \bigodot_{i=m_2}^{0}{\Post''_{3i}}\subst{{\Post''_2}}\bigodot_{j=m_1}^{0}\subst{{\Post''_{1j}}} \\
+%~~\qquad= \Post' \uplus \bigodot_{j=n}^{0} \Post_j $\\
 %\qed
@@
 \begin{align*}
-\alpha_Q=&\alpha'_Q\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}\\
-\set{\gamma}=&\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\!\!\bigotimes_{j=h-1}^{0}\!\! \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=k}^{0}\!\!\Post_{1j}}} \dotcup%\\
+\alpha_Q=&\alpha'_Q\displaystyle{\subst{\bigodot_{j=k}^{0}\Post_{1j}}}\\
+\set{\gamma}=&\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\!\!\bigodot_{j=h-1}^{0}\!\! \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigodot_{j=k}^{0}\!\!\Post_{1j}}} \dotcup%\\
 		%&
- \mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\!\!\bigotimes_{j=h-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=k}^{0}\Post_{1j}} }\\
-\Pred_Q=&\bigwedge_{h=0}^{k}\!\Pred_{1h}\subst{\!\!\bigotimes_{j=h-1}^{0}\!\!\!\!\Post_{1 j}}\land \Pred_2\subst{\bigotimes_{h=k}^{0}\Post_{1h}}\land%\\
+ \mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\!\!\bigodot_{j=h-1}^{0}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=k}^{0}\Post_{1j}} }\\
+\Pred_Q=&\bigwedge_{h=0}^{k}\!\Pred_{1h}\subst{\!\!\bigodot_{j=h-1}^{0}\!\!\!\!\Post_{1 j}}\land \Pred_2\subst{\bigodot_{h=k}^{0}\Post_{1h}}\land%\\
 %&
-	\!\bigwedge_{h=0}^{k'}\!\Pred_{3h}\subst{\!\! 	\bigotimes_{j=h-1}^{0}\!\!\!{\Post_{3j}}\otimes{\Post_2}  \otimes\bigotimes_{h=k}^{0}\!\!\Post_{1h}}\\
-\Post_Q=&\bigotimes_{h=k'}^{0}\!\!\Post_{3h}\otimes\Post_2\otimes\bigotimes_{j=k}^{0}\!\!\Post_{1j}
+	\!\bigwedge_{h=0}^{k'}\!\Pred_{3h}\subst{\!\! 	\bigodot_{j=h-1}^{0}\!\!\!{\Post_{3j}}\otimes{\Post_2}  \otimes\bigodot_{h=k}^{0}\!\!\Post_{1h}}\\
+\Post_Q=&\bigodot_{h=k'}^{0}\!\!\Post_{3h}\otimes\Post_2\otimes\bigodot_{j=k}^{0}\!\!\Post_{1j}
 \end{align*}
@@
 where ~~
-$\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$
+$\alpha'=\alpha\displaystyle{\subst{\bigodot_{j=k}^{0}\Post_{1j}}}$
 and $\alpha=\alpha'$  because $\Post_{1j}$ acts on variables of $Q$ and $\alpha$ contains only variables of $P$.
@@
 \begin{align*}
-\set{\gamma_c}=&\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{i=h-1}^{0}\!\!
-\Post_{1i} } }  \dotcup  \vis{({\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2})\subst{\bigotimes_{i=k}^{0}\Post_{1i}}} \dotcup\\
-&\mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{i=h-1}^{0}\!\!\Post_{3i}\shortotimes\Post_2\shortotimes\bigotimes_{i=k}^{0}\Post_{1i}} }\\
+\set{\gamma_c}=&\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigodot_{i=h-1}^{0}\!\!
+\Post_{1i} } }  \dotcup  \vis{({\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2})\subst{\bigodot_{i=k}^{0}\Post_{1i}}} \dotcup\\
+&\mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigodot_{i=h-1}^{0}\!\!\Post_{3i}\shortodot\Post_2\shortodot\bigodot_{i=k}^{0}\Post_{1i}} }\\
 =&\set{\gamma}\uplus\vis{\beta_j^{\in J\setminus \{j_0\}}} \quad  \text{ because $\Post_{1j}$  does not act on variables of $\beta_j$.}  
@@
 \Pred_c=&
-\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_{1i}}\land
-\left(Pred\land\Pred_2\land \alpha'_Q=\beta_{j_0}\right) \subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land\\
-&\bigwedge_{h=0}^{k'}{\Pred_{3h}}\subst{\bigotimes_{i=h-1}^{0}{\Post_{3i}}\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}
+\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigodot_{i=h-1}^{0}\Post_{1i}}\land
+\left(Pred\land\Pred_2\land \alpha'_Q=\beta_{j_0}\right) \subst{\bigodot_{i=k}^{0}{\Post_{1i}}}\land\\
+&\bigwedge_{h=0}^{k'}{\Pred_{3h}}\subst{\bigodot_{i=h-1}^{0}{\Post_{3i}}\shortodot({\Post\uplus \Post_2})\shortodot\bigodot_{i=k}^{0}{\Post_{1i}}}
 \\
-\Post_c=&(\bigotimes_{i=k'}^{0}{\Post_{3i}})\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}
+\Post_c=&(\bigodot_{i=k'}^{0}{\Post_{3i}})\shortodot({\Post\uplus \Post_2})\shortodot\bigodot_{i=k}^{0}{\Post_{1i}}
 \end{align*}
@@
 \begin{split}
-\Pred_c&=\Pred_Q\land\Pred\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land
-(\alpha'_Q=\beta_{j_0})\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\\
+\Pred_c&=\Pred_Q\land\Pred\subst{\bigodot_{i=k}^{0}{\Post_{1i}}}\land
+(\alpha'_Q=\beta_{j_0})\subst{\bigodot_{i=k}^{0}{\Post_{1i}}}\\
 &=\Pred_Q\land\Pred\land \alpha_Q=\beta_{j_0}\\[.3ex]
@@
 
-\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}\subst{\bigotimes_{k=p}^{0}{\Post_k}}}
-
-\Pred\,'=\Pred\land \bigwedge_{p=0}^{n}(\alpha_p=\beta_p\land \Pred_p)\subst{\bigotimes_{i=p-1}^{0}\Post_i}
-
-\Post\,'=\Post\uplus\bigotimes_{p=n}^{0}
+\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}\subst{\bigodot_{k=p}^{0}{\Post_k}}}
+
+\Pred\,'=\Pred\land \bigwedge_{p=0}^{n}(\alpha_p=\beta_p\land \Pred_p)\subst{\bigodot_{i=p-1}^{0}\Post_i}
+
+\Post\,'=\Post\uplus\bigodot_{p=n}^{0}
 		\Post_p
@@
 \forall i\in L.&~~s_i=s_{10 i} \wedge s_{1(m_1+1) i}=s_{20i} \wedge  s_{21i}= s_{30 i} \wedge s_{3(m_2+1) i}=s'_i\\
-\alpha=&\alpha'{\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \\
-\gamma_j^{j\in J}=&{\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigotimes_{k=i-1}^{0}\!\!
-\Post_{1k} } }  \dotcup \, \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigotimes_{k=m_1}^{0}\Post_{1k}}}}\, \dotcup\\
-&\mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{3p}} \subst{\bigotimes_{k=i-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}}\\
-\Pred=&{\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\subst{\!\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}\big)\land\Pred_2\subst{\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\land}%\\ 
+\alpha=&\alpha'{\subst{\bigodot_{j=m_1}^{0}\Post_{1j}}} \\
+\gamma_j^{j\in J}=&{\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigodot_{k=i-1}^{0}\!\!
+\Post_{1k} } }  \dotcup \, \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigodot_{k=m_1}^{0}\Post_{1k}}}}\, \dotcup\\
+&\mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{3p}} \subst{\bigodot_{k=i-1}^{0}\Post_{3k}\shortodot\Post_2\shortodot\bigodot_{k=m_1}^{0}\Post_{1k}}}\\
+\Pred=&{\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\subst{\!\bigodot_{j=p-1}^{0}\!\!\Post_{1j}}\big)\land\Pred_2\subst{\!\bigodot_{p=m_1}^{0}\!\!\Post_{1p}}\land}%\\ 
 %&
-{\bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\bigotimes_{j=p-1}^{0}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}}\\
-\Post=&{\bigotimes_{p=m_2}^{0}\Post_{3p}\otimes\Post_2\otimes\bigotimes_{j=m_1}^{0}\Post_{1j}}
+{\bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\bigodot_{j=p-1}^{0}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\bigodot_{p=m_1}^{0}\!\!\Post_{1p}}}\\
+\Post=&{\bigodot_{p=m_2}^{0}\Post_{3p}\otimes\Post_2\otimes\bigodot_{j=m_1}^{0}\Post_{1j}}
 \end{align*}
@@
 {\mybigdotcup_{\substack{i=0\\j_0\in J_{1i}}}^{m_1}\!\!\!
-\vis{{\beta_{1ij_0}}\subst{\!\bigotimes_{k=i-1}^{0} \!\!\!\!\Post_{1k} } }  \,\dotcup\, \vis{{\beta_{2j_0}}\subst{\!\bigotimes_{k=m_1}^{0}\!\!\!\Post_{1k}}}}\dotcup\!
+\vis{{\beta_{1ij_0}}\subst{\!\bigodot_{k=i-1}^{0} \!\!\!\!\Post_{1k} } }  \,\dotcup\, \vis{{\beta_{2j_0}}\subst{\!\bigodot_{k=m_1}^{0}\!\!\!\Post_{1k}}}}\dotcup\!
 %\\
 %&
-{ \!\mybigdotcup_{\substack{i=0\\j_0\in J_{3i}}}^{m_2}\!\! \vis{{\beta_{3ij_0}} \subst{\!\bigotimes_{k=i-1}^{0}\!\!\!\Post_{3k}\shortotimes\Post_2\shortotimes
-\!\!\bigotimes_{k=m_1}^{0}\!\!\!\Post_{1k}}}}
+{ \!\mybigdotcup_{\substack{i=0\\j_0\in J_{3i}}}^{m_2}\!\! \vis{{\beta_{3ij_0}} \subst{\!\bigodot_{k=i-1}^{0}\!\!\!\Post_{3k}\shortodot\Post_2\shortodot
+\!\!\bigodot_{k=m_1}^{0}\!\!\!\Post_{1k}}}}
 \end{align*}}
@@
 \noindent We have, by definition of $n_i$ and $n'_i$:\\
-$\displaystyle{\forall{i\in[0\,..\,m\!-\!1]}, \beta_{1 n_i j_0}\subst{\bigotimes_{k=n_i-1}^{0}\Post_{1k}}=\beta_i}$, \qquad$\displaystyle{\beta_{2 j_0}\subst{\bigotimes_{k=m_1}^{0} \Post_{1k} }=\beta_m}$, and \\
-$\displaystyle{\forall{i\in[m\!+\!1\,..\,n]}, \beta_{3 n_i' j_0}\subst{\bigotimes_{k=n_i'-1}^{0}\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\Post_{1k}}=\beta_i}$\\
+$\displaystyle{\forall{i\in[0\,..\,m\!-\!1]}, \beta_{1 n_i j_0}\subst{\bigodot_{k=n_i-1}^{0}\Post_{1k}}=\beta_i}$, \qquad$\displaystyle{\beta_{2 j_0}\subst{\bigodot_{k=m_1}^{0} \Post_{1k} }=\beta_m}$, and \\
+$\displaystyle{\forall{i\in[m\!+\!1\,..\,n]}, \beta_{3 n_i' j_0}\subst{\bigodot_{k=n_i'-1}^{0}\Post_{3k}\shortodot\Post_2\shortodot\bigodot_{k=m_1}^{0}\Post_{1k}}=\beta_i}$\\
 
@@
 \begin{align*}
-\alpha''=&\alpha'{\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}\\
+\alpha''=&\alpha'{\subst{\bigodot_{j=m_1}^{0}\Post'_{1j}}}\\
 \set{\gamma'}=&
- \mybigdotcup_{i=0}^{m_1}\set{\gamma'_{1i}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{1k}}\,\dotcup\,
-\set{\gamma'_{2}}\subst{\bigotimes_{k=m_1}^{0}\Post\,'_{1k}}\,\dotcup
- \mybigdotcup_{i=0}^{m_2}\set{\gamma'_{3i}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}
+ \mybigdotcup_{i=0}^{m_1}\set{\gamma'_{1i}}\subst{\bigodot_{k=i-1}^{0}\Post\,'_{1k}}\,\dotcup\,
+\set{\gamma'_{2}}\subst{\bigodot_{k=m_1}^{0}\Post\,'_{1k}}\,\dotcup
+ \mybigdotcup_{i=0}^{m_2}\set{\gamma'_{3i}}\subst{\bigodot_{k=i-1}^{0}\Post\,'_{3k}\shortodot\Post\,'_2\shortodot\bigodot_{k=n}^{0}\Post\,'_{1k}}
 \displaybreak[0]\\
-\Pred\,''=&\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\ 
-&\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_2}^{0}\Post\,'_{1j}}\displaybreak[0]\\
-\Post\,''=&\bigotimes_{j=m_2}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}
+\Pred\,''=&\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigodot_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigodot_{j=m_1}^{0}\Post\,'_{1j}}\land\\ 
+&\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigodot_{j=i-1}^{0}\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_2}^{0}\Post\,'_{1j}}\displaybreak[0]\\
+\Post\,''=&\bigodot_{j=m_2}^{0}\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{0}\Post\,'_{1j}
 \end{align*}
@@
 {\small \begin{align*}
-\alpha''&=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}}\\
-& = \alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}}&\text{$\alpha'$ only contains variables of $P$ untouched by $\Post_i$}\\
+\alpha''&=\alpha'\displaystyle{\subst{\bigodot_{j=m_1}^{0}\Post\,'_{1j}}}\\
+& = \alpha'\displaystyle{\subst{\bigodot_{j=m_1}^{0}\Post_{1j}}}&\text{$\alpha'$ only contains variables of $P$ untouched by $\Post_i$}\\
 & = \alpha
@@
 {\small \begin{equation*}
-\begin{split}\gamma'_j=&\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}}\subst{\bigotimes_{k=i-1}^{0}\! \Post_{1k} } }  \dotcup  \vis{{\beta_{2j}}\subst{\bigotimes_{k=m_1}^{0}\!\Post_{1k}}}\, \dotcup
-\mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij} \subst{\!\bigotimes_{k=i-1}^{0}\!\!\!\Post_{3k}\shortotimes\Post_2\shortotimes\bigotimes_{k=m_1}^{0}\!\!\Post_{1k}}}
+\begin{split}\gamma'_j=&\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}}\subst{\bigodot_{k=i-1}^{0}\! \Post_{1k} } }  \dotcup  \vis{{\beta_{2j}}\subst{\bigodot_{k=m_1}^{0}\!\Post_{1k}}}\, \dotcup
+\mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij} \subst{\!\bigodot_{k=i-1}^{0}\!\!\!\Post_{3k}\shortodot\Post_2\shortodot\bigodot_{k=m_1}^{0}\!\!\Post_{1k}}}
 \end{split}
@@
 \gamma'_j =&
-\mybigdotcup_{i=0}^{m_1}{\gamma'_{1ij}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{1k}}\dotcup
- {\gamma'_{2 j}}\subst{\bigotimes_{k=m_1}^{0}\Post\,'_{1k}}\,\dotcup\, \mybigdotcup_{i=0}^{m_2}{\gamma'_{3ij}}\subst{\bigotimes_{k=i-1}^{0}\Post\,'_{3k}\shortotimes\Post\,'_2\shortotimes\bigotimes_{k=n}^{0}\Post\,'_{1k}}\\
+\mybigdotcup_{i=0}^{m_1}{\gamma'_{1ij}}\subst{\bigodot_{k=i-1}^{0}\Post\,'_{1k}}\dotcup
+ {\gamma'_{2 j}}\subst{\bigodot_{k=m_1}^{0}\Post\,'_{1k}}\,\dotcup\, \mybigdotcup_{i=0}^{m_2}{\gamma'_{3ij}}\subst{\bigodot_{k=i-1}^{0}\Post\,'_{3k}\shortodot\Post\,'_2\shortodot\bigodot_{k=n}^{0}\Post\,'_{1k}}\\
 =&
-{\mybigdotcup_{t=0}^{n} {\gamma_{tj}}\subst{\bigotimes_{k=t-1}^{0} \Post_{k}}}   
+{\mybigdotcup_{t=0}^{n} {\gamma_{tj}}\subst{\bigodot_{k=t-1}^{0} \Post_{k}}}   
 \end{split}
@@
 %\begin{split}
-%\Pred\,''&=\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land\\
-%&~~{\bigwedge_{i=0}^{m_3}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}}\\
-%&=\big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\land\Pred_2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\
-%&~~~\bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}\big) \land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\Post_i \land
-%%$~\qquad\qquad\,\displaystyle{\bigwedge_{i=0}^{m-1}(\beta_{1{n_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j={n_i}-1}^{0}\Post\,'_{1j}}\land(\beta_{2{j_0}}=\alpha_m) \subst{\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\land}
+%\Pred\,''&=\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigodot_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigodot_{j=m_1}^{0}\Post\,'_{1j}}\land\\
+%&~~{\bigwedge_{i=0}^{m_3}\Pred\,'_{3i}\subst{\bigodot_{j=i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigodot_{j=m_1}^{0}\Post\,'_{1j}}}\\
+%&=\big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\bigodot_{j=p-1}^{0}\Post_{1j}}\land\Pred_2\subst{\bigodot_{p=m_1}^{0}\Post_{1p}}\land\\
+%&~~~\bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigodot_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigodot_{p=m_1}^{0}\Post_{1p}}\big) \land \bigwedge_{t=0}^{n} \Pred_t\bigodot_{i=t-1}^{0}\Post_i \land
+%%$~\qquad\qquad\,\displaystyle{\bigwedge_{i=0}^{m-1}(\beta_{1{n_i}{j_0}}=\alpha_i)\subst{\bigodot_{j={n_i}-1}^{0}\Post\,'_{1j}}\land(\beta_{2{j_0}}=\alpha_m) \subst{\bigodot_{j=m_1}^{0}\Post\,'_{1j}}\land}
 %\end{split}
 %\end{equation*}
-%%$~\qquad\qquad\,\displaystyle{\bigwedge_{i=m+1}^{n}(\beta_{3{n'_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j=n'_i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}}\Big)}$\\
+%%$~\qquad\qquad\,\displaystyle{\bigwedge_{i=m+1}^{n}(\beta_{3{n'_i}{j_0}}=\alpha_i)\subst{\bigodot_{j=n'_i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigodot_{j=m_1}^{0}\Post\,'_{1j}}\Big)}$\\
 %\end{small}
@@
 \begin{align*}
-\Pred\,''&=\Big(\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}\land%\\ &\qquad
+\Pred\,''&=\Big(\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}}\land%\\ &\qquad
 %~\quad
-\bigwedge_{i=0}^{m_3}\Pred\,'_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\Post\,'_{1j}}\Big)\\
-&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}\land\Pred_2\subst{\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\Big)\\&\qquad
-\land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\!\!\Post_i%\\&\qquad
-\land \Big( \bigwedge_{i=0}^{m-1}(\beta_{1{n_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j={n_i}-1}^{0}\Post\,'_{1j}}\land(\beta_{2{j_0}}=\alpha_m) \subst{\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}\land\\ &\qquad
-~\quad\bigwedge_{i=m+1}^{n}(\beta_{3{n'_i}{j_0}}=\alpha_i)\subst{\bigotimes_{j=n'_i-1}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post\,'_{1j}}\Big)\displaybreak[0]\\
-&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{1j}}\big)\land\Pred_2\subst{\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\!\bigotimes_{j=p-1}^{0}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\!\bigotimes_{p=m_1}^{0}\!\!\Post_{1p}}\Big)\\&\qquad
-\land \bigwedge_{t=0}^{n} \Pred_t\bigotimes_{i=t-1}^{0}\!\!\Post_i
-\land \Big(\bigwedge_{i=0}^{m-1}(\beta_{i}=\alpha_i)\subst{\bigotimes_{j={i-1}}^{0}\!\!\Post_{j}}\land(\beta_m=\alpha_m )\subst{\bigotimes_{j=m}^{0}\Post_{j}}\land\\ &\qquad
-~\quad\bigwedge_{i=m+1}^{n}(\beta_i=\alpha_i)\subst{\bigotimes_{j=i-1}^{m}\!\!\Post_j\shortotimes\Post_m\shortotimes\bigotimes_{j=m-1}^{0}\!\!\Post_{j}}\Big)\\
+\bigwedge_{i=0}^{m_3}\Pred\,'_{3i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{0}\!\Post\,'_{1j}}\Big)\\
+&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\!\!\bigodot_{j=p-1}^{0}\!\!\Post_{1j}}\land\Pred_2\subst{\!\!\bigodot_{p=m_1}^{0}\!\!\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\!\bigodot_{j=p-1}^{0}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\!\bigodot_{p=m_1}^{0}\!\!\Post_{1p}}\Big)\\&\qquad
+\land \bigwedge_{t=0}^{n} \Pred_t\bigodot_{i=t-1}^{0}\!\!\Post_i%\\&\qquad
+\land \Big( \bigwedge_{i=0}^{m-1}(\beta_{1{n_i}{j_0}}=\alpha_i)\subst{\bigodot_{j={n_i}-1}^{0}\Post\,'_{1j}}\land(\beta_{2{j_0}}=\alpha_m) \subst{\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}}\land\\ &\qquad
+~\quad\bigwedge_{i=m+1}^{n}(\beta_{3{n'_i}{j_0}}=\alpha_i)\subst{\bigodot_{j=n'_i-1}^{0}\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}}\Big)\displaybreak[0]\\
+&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\!\!\bigodot_{j=p-1}^{0}\!\!\Post_{1j}}\big)\land\Pred_2\subst{\!\!\bigodot_{p=m_1}^{0}\!\!\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\!\bigodot_{j=p-1}^{0}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\!\bigodot_{p=m_1}^{0}\!\!\Post_{1p}}\Big)\\&\qquad
+\land \bigwedge_{t=0}^{n} \Pred_t\bigodot_{i=t-1}^{0}\!\!\Post_i
+\land \Big(\bigwedge_{i=0}^{m-1}(\beta_{i}=\alpha_i)\subst{\bigodot_{j={i-1}}^{0}\!\!\Post_{j}}\land(\beta_m=\alpha_m )\subst{\bigodot_{j=m}^{0}\Post_{j}}\land\\ &\qquad
+~\quad\bigwedge_{i=m+1}^{n}(\beta_i=\alpha_i)\subst{\bigodot_{j=i-1}^{m}\!\!\Post_j\shortodot\Post_m\shortodot\bigodot_{j=m-1}^{0}\!\!\Post_{j}}\Big)\\
 &=\Pred
@@
 \begin{split}
-\Post\,''&=\bigotimes_{j=m_2}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}\\
-&=\left(\bigotimes_{j=m_2}^{0}\Post\,'_{3j}\shortotimes\Post\,'_2\shortotimes\bigotimes_{j=m_1}^{0}\Post\,'_{1j}\right)\uplus \bigotimes_{j=n}^{0}\Post_j\\
-&=\Post \uplus \bigotimes_{j=n}^{0}\Post_j\
+\Post\,''&=\bigodot_{j=m_2}^{0}\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{0}\Post\,'_{1j}\\
+&=\left(\bigodot_{j=m_2}^{0}\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{0}\Post\,'_{1j}\right)\uplus \bigodot_{j=n}^{0}\Post_j\\
+&=\Post \uplus \bigodot_{j=n}^{0}\Post_j\
 \end{split}
@@
 %More tricky, they do not have the same state variables, as 202 has the variables of state $s2$, but none of these variables are used in transitions from 202.
-In this configuration we can guarantee that they are Weak bisimilar, and we have merged their (incoming and outgoing) transitions in the figure. We denote this 
+In this configuration we can guarantee that they are weak bisimilar, and we have merged their (incoming and outgoing) transitions in the figure. We denote this 
 equivalence class of states as $\{000,202\}$.
@@
 \begin{align*}
-Post_{6a}&=\ post_{4}\shortotimes\ post_{456}^*\shortotimes\ post_{6}\\
+Post_{6a}&=\ post_{4}\shortodot\ post_{456}^*\shortodot\ post_{6}\\
 &= \left( (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec})
-\shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+n) \right)
-\shortotimes (\texttt{s\_ec}\gets \texttt{s\_ec}+1) \\
+\shortodot (\texttt{s\_ec}\gets \texttt{s\_ec}+n) \right)
+\shortodot (\texttt{s\_ec}\gets \texttt{s\_ec}+1) \\
 &= (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets (\texttt{s\_ec}+1)+n, \texttt{s\_ec}\gets (\texttt{s\_ec}+1)+n)
@@
 
-         Note: if we were using the alternative Weak bisimulation relation from Appendix \ref{app-WFH-equiv}, Lemma \ref{lem-rel-OT-WOT}, that is checking strong bisimulation between the corresponding
+         Note: if we were using the alternative weak bisimulation relation from Appendix \ref{app-WFH-equiv}, Lemma \ref{lem-rel-OT-WOT}, that is checking strong bisimulation between the corresponding
 weak automaton, we would have a more transitions coverage to examine, as we have 4 weak transitions for $b0$ in the \symb{SimpleProtocolSpec} weak automaton, and 7 WOTs (including 4 

### 2021-10-08 2016-Weak-FH-Bisim/WeakBisim.tex
typos mineurs

@@
 For any open transition $OT_{px}$, since
-       	$(t_p,u|\Pred_{p,u})\in\mathcal{R}'$ there exist open transitions
+       	$(t_p,u|\Pred_{p,u})\in\mathcal{R}'$ there exists an indexed set of open transitions
        	$OT_{pxy}^{y\in Y} \subseteq \mathcal{T}_3$:
@@
 Modulo renaming of fresh variables, this is identical to the predicate that 
-occurs in 
-the source open transition except $\alpha_{j_0}=\alpha'_{j_0}$ has been replaced by  
-$\beta_{j_0}=\alpha'_{j_0}$. As $\alpha_{j_0}=\alpha_Q$ and $\beta_{j_0}$ is free, we 
-have $\beta_{j_0}=\alpha'_{j_0}\land \beta_{j_0}=\alpha_Q \iff 
-\alpha_{j_0}=\alpha'_{j_0}$.
+occurs in the source open transition except $\alpha_{j_0}=\alpha'_{j_0}$ has been replaced by  $\beta_{j_0}=\alpha'_{j_0}$.
+As $\alpha_{j_0}=\alpha_Q$ and $\beta_{j_0}$ is free, we have $\beta_{j_0}=\alpha'_{j_0}\land \beta_{j_0}=\alpha_Q \iff \alpha_{j_0}=\alpha'_{j_0}$.
 Thus, $\Pred \iff (\Pred\,'
@@
 into conditions of the context $P$ and the pNet $Q$ (they are
-builts similarly as they only deal with  
+built similarly as they only deal with  
 leaves): $\Post=\Post\,'\uplus \Post\,''$. This concludes the 
 proof as we checked all the premises of the open transition for both $P$ and $Q$. We obtain the following reduction by the rule \TrDeux:
+\medskip
+
 \noindent
@@
     		\!\!\!\!\!\Post_m = 	\Post\uplus \Post\,'}$.\\ Finally, the composed open transition can be
-        built by \TrDeux\ as follows
+        built by \TrDeux\ as follows:
 	\noindent
@@
 \end{mathpar}
-Then, for any state $\ostate{s_i^{i\in L_Q}}$ of $Q$, we have\\[-1ex]
+Then, for any state $\ostate{s_i^{i\in L_Q}}$ of $Q$, we have:\\[-1ex]
 	\[ P[Q]_{j_0}  
@@
  Let $J'=J\setminus \Holes(Q) \cup \{j_0\}$.	 By 
- Lemma~\ref{lem-decompose} we have :\\[-2ex]
+ Lemma~\ref{lem-decompose} we have:\\[-2ex]
  	\begin{mathpar}
@@
 Let $J'=J\setminus \Holes(Q) \cup \{j_0\}$.	 By 
-	Lemma~\ref{lem-decompose} we have :\\[-2ex]
+	Lemma~\ref{lem-decompose} we have:\\[-2ex]
 			\begin{mathpar}
@@
 \noindent ($\Leftarrow$) We proceed by structural induction on the rules  building  the weak transition (as described in the original definition).
-The recurrence hypothesis being that the  the original definition implies the characterization (1),with the conditions stated at the bottom of the theorem.
+The recurrence hypothesis being that the  the original definition implies the characterization (1), with the conditions stated at the bottom of the theorem.
 We consider the different rules:
@@
 \end{mathpar}
- there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
+ there exists an indexed set of weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
  \begin{mathpar}
@@
 
-Else $Q$ does not move and we have \\
+Else $Q$ does not move and we have: \\
 $\begin{small} P\models{\openrule
@@
 }
-Next, we have
+Next, we have:
 \[\Pred = \displaystyle{\Pred\,'
@@
 \end{align*}}
-Which concludes because we have we have $\displaystyle{\bigodot_{j=n'_{k}-1}^{0}\!\!\Post\,''_{j} = \bigodot_{j=k-1}^{0}\!\!\Post_{j}}$.
+Which concludes because  we have $\displaystyle{\bigodot_{j=n'_{k}-1}^{0}\!\!\Post\,''_{j} = \bigodot_{j=k-1}^{0}\!\!\Post_{j}}$.
 %
@@
 
-Then, we have
+Then, we have:
 {\small	\[ P[Q]_{j_0}  
@@
 \end{mathpar}
-Then, we have
+Then, we have:
 	\[ P[Q]_{j_0}  
@@
 
- First suppose $j\in J\setminus\{j_0\}$ we have $\gamma'_j=\gamma_j$ because $\Post^{\,\prime}_{ij}$ has no effect on variables of $P$ and on $\beta_{1pj}$, consequently\\
+ First suppose $j\in J\setminus\{j_0\}$ we have $\gamma'_j=\gamma_j$ because $\Post^{\,\prime}_{ij}$ has no effect on variables of $P$ and on $\beta_{1pj}$, consequently we have:\\
 {\small \begin{equation*}
@@
  \begin{proof}   Consider $P$ weak FH-bisimilar to $P'$.
-There exist a FH-bisimulation $\mathcal{R}_{P,P'}$ relating $P$ and $P'$.
+There exists a FH-bisimulation $\mathcal{R}_{P,P'}$ relating $P$ and $P'$.
 We define a relation $\mathcal{R}$ relating states of $P[Q]_{j_0}$ with states of $P'[Q]_{j_0}$:

### 2021-10-08 2016-Weak-FH-Bisim/WeakBisim.tex
minor

--- 2021-10-06 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 \begin{definition}[Semantics of pNets as a weak open automaton]
-Let $A$ be the open automaton expressing the semantics of an open pNet $\pNet$; let $\mylangle J,\mathcal{S},s_0, V, \WT\myrangle$ be the weak open automaton derived from $A$; this weak open automaton defines the weak semantics of the pNet $\pNet$.
+Let $A$ be the open automaton expressing the semantics of an open pNet $\pNet$; let $\mylangle J,\mathcal{S},s_0, V, \WT\myrangle$ be the weak open automaton derived from $A$; we call this weak open automaton the weak semantics of the pNet $\pNet$.
 Then, we denote $\pNet \models \WOT$ whenever $\WOT\in\WT$.

### 2021-10-08 2016-Weak-FH-Bisim/2021-09-letter2Reviewers.tex
letter and CCS

@@
 \usepackage{a4wide}
+\usepackage{macrospNets}
+
 \title{Reply to reviewers\\
@@
 \section*{Annex 1: response to first reviewers' comments}
+
 - The definition of pNets is cumbersome.
@@
 It would perhaps be useful to provide anecdotal evidence showing that comparable formalisms cannot handle certain features of the example (which would justify the complexity of the model used).
+\begin{quote}
+The definition of pNets is indeed not simple but as it is placed at a very generic and semantic level we do not believe there are good alternative in the literature.
+Process algebras for example do not feature hierarchical an parametric aspects of pNets and defining equivalence checking tools on these frameworks is difficult.
+Of course the examples can be expressed in any concurrent Turing-complete model but none of the existing works feature the same results as ours on the modelling of existing parallel operators, and compositional reasoning on equivalence.
+
+We added most of these arguments in the introduction, and the related work section discusses details on equivalence checking.
+We also discuss in more details the relation with process algebras in the paper.
+\end{quote}
 
@@
 1) How do you validate the translation of pNets to Open Automata?  Shouldn't there be some result that states that the translation is semantic preserving?   
+\begin{quote}
+Indeed such a theorem could be stated and proven: the two semantics are behaviourally equivalent, this would be proven by exhibiting a complex bisimulation between the two models, restricted only on the closed non-parametric part.
+In practice a proof of equivalence would make the article much longer with a lot of technical developments; we believe it would make the article more difficult to read.
+However we added a discussion on equivalence between semantics at the end of Section 2.2.
+\end{quote}
+
 2) Why not work directly in terms of Open Automata (and forget all about pNets)?
@@
 There are few people who would be interested in using a framework that relies on the second rule in Def 9 as a modelling language...
+\begin{quote}
+The reason for the coexistence of the two formalisms is that one is hierarchical and adapted to modelling, the other is flat and more based on logic, and adapted to semantic/equivalence reasoning.
+We added one subsection in the introduction that presents the two formalisms and the reason why both exist.
+\end{quote}
 
@@
 Moreover, given that a set is required, shouldn't there be an additional requirement that the matching set is necessarily non-empty?
+
+\begin{quote}
+The following explanation has been added to the introduction:
+
+" Bisimulation over a symbolic and open model like open pNets or open automata is  different from the classical notion of bisimulation because it cannot rely on the equality over a finite set of action labels.
+Classical bisimulations require to exhibit, for each transition of one system, a transition of the other system that simulates it.
+Instead, bisimulation for open automata  rely on the simulation of each open transition of one automaton by a set of open transitions of the other one, that should cover all the
+cases where the original transition can be triggered.
+"
+
+Concerning non-emptiness, the fact that the matching set of transitions completely cover the cases of the original ones by nature prevent the empty set from being a good match. 
+\end{quote}
 
@@
 
+\begin{quote}
+Indeed, the plus operator of CCS does not verify the requirements ``non-observability of tau transitions'' for the weak bisimulation to be a congruence.
+We can define the weak bisimulation for CCS but it does not verify the congruence property.
+
+This is now illustrated by Example 4 and 5 in the article.
+\end{quote}
+
+l -6: why not use an asymmetric symbol instead of $\otimes$? 
+QUESTION: veut on vraiment changer de symbole?
+ANSWER:
+\begin{quote}
+$\otimes$ is a form of composition: we chose something similar to $\circ$, re named it into $\odot$
+\end{quote}
+
+l 26: "Variables in V1 and V2 verify the predicate $P_{s,t}$" I am not sure what you mean by this.
+\begin{quote}
+This has been rephrased:
+
+the states are related when the value of the variables in $s$ and $t$  verify the predicate $\Pred_{s,t}$. Note that this implies that the free variables of  $\Pred_{s,t}$ belong to $V_1$ and $V_2$.
+
+\end{quote}
+
+l 27..28: why should V1 and V2 be disjoint?
+\begin{quote}
+Variables used in $\Pred_{s,t}$ should refer to variables of the automata, but there must be no ambiguity on which automaton it refers to.
+If the variable x should have the same value in both automata, we add x=x' to Pred.
+Otherwise hidden information would be confusing and the soundness of the theory would be difficult to ensure.
+
+We explained this point better in the text
+\end{quote}
+
+pg 14:  why is the term "Specification pNet" capitalised?
+\begin{quote}
+Indeed, we renamed in a consistent manner all our examples
+\end{quote}
+
+pg 17: l -4: I found this condition hard to map to the intuition given on pg 18 line 1..2 
+\begin{quote}
+We explicitly added the following explanation:
+
+statement (2) states that all the open transitions where a hole does  a $\tau$ must be of the shape given in statement (1)
+\end{quote}
+
 \section*{Annex 2: response to second reviewers' comments}
+SYNOPSIS
+
+The paper proposes a generalisation of transition system specification (well known in the literature on structural operational semantics) called an open automaton, that generalises the traditional transition systems in two dimensions: hierarchical composition and conditional transition that may update the variables once the transition is executed (akin to extended finite state machines).
+The paper mainly uses open automata for semantic purposes: first, to define the semantics of parametrised networks (a graph-theoretic specification language); second, to define the (weak) bisimulation relations on the states of open automata (in turn between the states of a parametrised network).
+Lastly, congruence results are established both for strong and weak bisimulation relations w.r.t.
+the hierarchical composition operator.
+
+EVALUATION
+
+The paper is fairly well written and clearly falls in the scope of the journal LMCS; however, it comes short in reaching the quality transpired by an LMCS journal.
+The introduction needs an improvement especially in terms of motivation; this seems to be the case with the formal definitions which in some cases need to be properly defined (see the detailed comments).
+For e.g., why were pNets introduced?
+
+Since pNets have been introduced for over 15 years, why are we studying (weak) bisimulation and establishing the usual basic facts about it now?
+Were there any case studies in your experience that suggest the need for such results?
+What are the reasons to pick bisimulation not simulation relations for the purpose of conformance between a specification and its implementation?
+It would be great to support these with some evidence.
+
+\begin{quote}
+pNets had been used to do model-checking based on the translation (of closed pNets with parameters instantiated) to other formalisms, we now study them directly.
+We decided to first design an equivalence relation before orders that reveal to be more complex (simulation is discussed in our new conclusion).
+In our example it happens that we have weak equivalence which is stronger than weak simulation in any case.
+\end{quote}
+
+Secondly, the choices made behind the mathematical notations and definitions are at a low level of abstraction; unfortunately, which makes the proofs in the appendix as unreadable.
+This is disappointing since most of the theorem/lemma statements are those that one would expect to be true.
+
+In addition, purely from the semantic point of view, the theoretical development is rather straightforward and most of the definitions/results already known in the literature on process algebras are engineered to the setting of open automata.
+\begin{quote}
+We believe that this argument is rather subjective.
+From an objective point of view, the parameterised aspects of our model is from our point of view quite new, as well as the conditions for congruence of weak bisimulation.
+We added arguments highlighting the novelty in the introduction.
+\end{quote}
+
+As a result, unfortunately, I do not endorse the publication of this manuscript.
+Nevertheless, I do believe that the paper may be more fitting in a journal which endorses both software engineering and formal methods.
+
 DETAILED COMMENTS
@@
 
-P9 Def 6 L-2 open with capital O
+\begin{quote}
+We rephrased quite a lot this part in particular we write now:
+
+It is important to understand the difference between the red dotted rule and a normal 
+inference rule. They correspond to two different logical levels.
+On one side, classical (black) inference rules  use  an expressive logic (like any other computer science article).
+ On the other side, open transition rules (with dotted lines) are logical implications, but using a  logic with a specific syntax and that can be mechanized (this logic includes the boolean expressions $\AlgB$, boolean operators, and term equality).
+\end{quote}
 
@@
 refinement of predicates, which is a strong assumption from the modelling point of view. This is because modeller is forced to add new behaviour which (s)he is not interested to capture.
+\begin{quote}
+We slightly rewrote this part and we now explicitly say that in practice, in the tools, we have a finite representation of the transitions and thus we only interact with the user based on this finite representation (see the paragraph between Theorem 1 and Theorem 2).
+In any case, the written closure, in general, has no finite representation.
+
+From the point of view of the article, proofs are simpler to write if we suppose that  the set of open transitions is closed under the
+refinement of predicates.
+\end{quote}
+
 Lastly, I was anticipating a more formal way to derive transitions of an open automaton just like how transitions are derived by a witnessing proof in the context of transition system specifications.
@@
 
-P10 Def 7 L-6 Typo *!J* should be just *J*
+\begin{quote}
+We explain now the relation with GSOS and negative premisses in the related works
+\end{quote}
 
@@
 
+\begin{quote}
+We added the formal definition of $R$  before the definition of FH-bisimulation.
+Basically, in our case $L$ are the boolean expressions, denoted $B$, and corresponding to the set of all possible predicates.
+We believe the powerset is bigger that what we do, and we do not allow a pair of states to be matched to several Predicates.
+In one word the relation is now typed (with side constraints), see the details in the text.
+
+We also briefly compare to the cited article in the related work section.
+
+\end{quote}
+
 P11 L1 What is X in the open transition $OT_x^{x\in X}$?
+\begin{quote}
+In the context of this article, we consider that an indexed set $OT_x^{x\in X}$ defines both an indexation set $X$ and a set of elements $OT_x$ for $x\in $.
+We additionally clarified this in the notation section.
+Additionally to the previous text that stated:
+"$t_i^{i\in I}$ defines first $I$ the set over which the family is indexed, and then $a_i$ the elements of the family"
+we added:
+"Note that, sentences of the form ``there exists $t_i^{i\in I}$'' means there exists $I$ and a function that maps each element of $I$ to a term $t_i$."
+\end{quote}
 
 P11 L2 Typo: jx as the subscript of \\beta. You could use $\beta_{j_x}$?
+\begin{quote}
+We should have standardly written $\beta_{j,\, x}$ but the multiplicity of commas would make the article difficult to read. We add the following footnote:
+``In this article, we denote $\beta_{j x}$  a double indexed set, instead of the classical $\beta_{j,\, x}$. Indeed the standard notation would be too heavy in our case.''
+\end{quote}
 
@@
 
-P13 Def 9 In the first line of the premise of Tr2, shouldn’t the occurrences of $\alpha’ in SV_k just be \alpha$?
+P13 Def 9 In the first line of the premise of Tr2, shouldn’t the occurrences of $\alpha’$ in $SV_k$ just be $\alpha$?
+\begin{quote}
+
+No, we have the constraint $\alpha=\alpha'$, but as actions are parameterised it corresponds to some instantiation and unification.
+For example in the simple protocol we would have $\alpha=in(m)$ and $\alpha'= in(MSG)$ with $MSG$ a real message object, obtained by the r-send transition of the receiver automaton.
+\end{quote}
 
 P13 Def 9 Tr2 by *$fresh(\alpha’_m,\alpha’,\beta_j,\alpha)$* should be understand that the variables occurring in $\alpha’_m,\alpha’, \beta_j$ (for all j), and $\alpha$ are fresh?
+\begin{quote}
+It is written just above the definition
+\end{quote}
 
@@
 First, whether a similar result holds for simulation?
-Second, FH-simulaton would be more relevant if we
+Second, FH-simulation would be more relevant if we
 disallow that the set of transitions in an open automaton are closed under the refinement of predicates (Def. 6).
+\begin{quote}
+See above: simulation is more complex and is discussed in the conclusion.
+\end{quote}
 
 P17 Def 11 Isn’t (1) a special case of (2)?
+\begin{quote}
+No because $T=\emptyset$ verifies (2) but not (1).
+We added an explanatory sentence below.
+\end{quote}
 
 P18 Def 12 Other than the symbol used for weak transition, is there any semantic difference in Def 12 between a weak open transition and an open transition defined earlier?
-
-P22 L-1 Shouldn’t Pred be $Pred_{s,t}$? Again, please give the type of this conditional relation
-
-P28 L2 *principle* --> *relations*
+\begin{quote}
+"$\gamma$ ranges over sequences of action terms while "$\beta$ ranges over action terms"
+This is now recalled before the definition.
+This has a huge semantic impact as a single weak transition is the composition of several transitions of the holes.
+\end{quote}
 

### 2021-10-08 2016-Weak-FH-Bisim/WeakBisim.tex
letter and CCS

@@
   verify the predicate $\Pred_{s,t}$. 2) The free variables of  $\Pred_{s,t}$ belong to $V_1$ and $V_2$, i.e. $\vars(\Pred_{s,t})\subseteq V_1\cup V_2$.
- FH-bisimulation is defined formally: 
+ FH-bisimulation is defined formally\footnote{In this article, we denote $\beta_{j x}$  a double indexed set, instead of the classical $\beta_{j,\, x}$.
+Indeed the standard notation would be too heavy in our case.}:
  \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim} ~\\
@@
 
+\begin{example}[CCS choice (counter-example)]\label{ex:CCSplus}
+Here is the encoding of a choice operator.\\[1.5ex]
+\begin{tabular}{cp{.52\linewidth}}
+ \begin{minipage}{.46\linewidth}
+ \includegraphics[width=\linewidth]{XFIG/Choice.pdf}\vspace{-18ex}
+\end{minipage} 
+&
+The left hole is
+  indexed $l$ the right hole $r$. The third subnet, contains an LTS encoding
+  the control part. We obtain the specific behaviour with the 
+  synchronisation vector. The first action  of one of
+  the holes decides which branch of the LTS is activated;
+   all subsequent actions will be from the same side. 
+\\
+\end{tabular}
+
+This pNet does not satisfy Definition~\ref{def:non-obspNet}. Indeed, if $a$ or $b$ is $\tau$ then the $+$ operator can indeed observe the $\tau$ transition.
+On the other side, the parallel operator defined similarly \emph{satisfies} Definition~\ref{def:non-obspNet}.
+
+\end{example}
+
 With this definition, it is easy to check that the open automaton that gives the semantics of such an open pNet cannot observe silent actions in the sense of Definition~\ref{def:Non-ObsTau}.
@@
 From the definition of the weak open automata of pNets, we can now study the properties of weak bisimulation concerning open pNets.
-
- \TODO{a counter example in  CCS}
 
@@
 
-\TODO{Conclude with CCS as an example}
+\begin{example}[CCS Choice] Consider the $+$ operator of CCS,shown in  Example~\ref{ex:CCSplus}.
+It is well-known that weak bisimulation is not a congruence in CCS, and this is reflected here because we have shown that the $+$ operator can observe the $\tau$ transitions.
+Thus, even if we can define a weak bisimulation for CCS with $+$ it does verify the necessary requirements for being a congruence.
+\end{example}
+
 \subsubsection*{Running example}

### 2021-10-10 2016-Weak-FH-Bisim/2021-09-letter2Reviewers.tex
Fini la "Letter to reviwers, et ajoute quelques changements mineurs dans le papier
Il reste 2 TODO dans la lettre, et j'ai un Pb sur la cherence des definitions/usages de Sort, 2 TODO dans le papier.

@@
 \usepackage{macrospNets}
+\usepackage{color}
+\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
+\newcommand{\NOTE}[1]{\textcolor{blue}{\textbf{[NOTE:#1]}}}
+\newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
 
@@
 \begin{quote}
-The definition of pNets is indeed not simple but as it is placed at a very generic and semantic level we do not believe there are good alternative in the literature.
-Process algebras for example do not feature hierarchical an parametric aspects of pNets and defining equivalence checking tools on these frameworks is difficult.
+The definition of pNets is indeed not simple but as it is placed at a very generic and semantic leve,l we do not believe there are good alternatives in the literature.
+Process algebras for example do not feature the hierarchical and parametric aspects of pNets and defining equivalence checking tools on these frameworks is difficult.
 Of course the examples can be expressed in any concurrent Turing-complete model but none of the existing works feature the same results as ours on the modelling of existing parallel operators, and compositional reasoning on equivalence.
@@
 
-Concerning non-emptiness, the fact that the matching set of transitions completely cover the cases of the original ones by nature prevent the empty set from being a good match. 
+Concerning non-emptiness, the fact that the matching set of transitions completely cover the cases of the original ones by nature prevents the empty set from being a good match. 
 \end{quote}
@@
 We can define the weak bisimulation for CCS but it does not verify the congruence property.
+\TODO{define the bisimulation, or encode the nondeterministic choice operator ?}
 
@@
 l -6: why not use an asymmetric symbol instead of $\otimes$? 
-QUESTION: veut on vraiment changer de symbole?
-ANSWER:
+%QUESTION: veut on vraiment changer de symbole?
+A%NSWER:
 \begin{quote}
-$\otimes$ is a form of composition: we chose something similar to $\circ$, re named it into $\odot$
+$\otimes$ is a form of composition: we have changed for something similar to $\circ$, renamed it into $\odot$
 \end{quote}
@@
 pNets had been used to do model-checking based on the translation (of closed pNets with parameters instantiated) to other formalisms, we now study them directly.
-We decided to first design an equivalence relation before orders that reveal to be more complex (simulation is discussed in our new conclusion).
+We decided to first design an equivalence relation rather than  preorders that reveal to be more complex (simulation is discussed in our new conclusion).
 In our example it happens that we have weak equivalence which is stronger than weak simulation in any case.
@@
 We believe that this argument is rather subjective.
-From an objective point of view, the parameterised aspects of our model is from our point of view quite new, as well as the conditions for congruence of weak bisimulation.
+From an objective point of view, the parameterised aspects of our model are from our point of view quite new, as well as the conditions for congruence of weak bisimulation.
 We added arguments highlighting the novelty in the introduction.
@@
 DETAILED COMMENTS
+\begin{quote}
+In the following, we simply removed from the list the comments for typos that we have directly corrected.
+\end{quote}
 
 P1 Abstract L10 *… that includes parameters, and …* parameters for what? Please elaborate more on this in the introduction.
+\begin{quote}
+This has been reworded.
+\end{quote}
 
 P2 L24 *… provides a cleaner version…* I am afraid such a sentence does not add any value if there is no explanation discussing it in detail somewhere later in the paper.
+\begin{quote}
+We change this for a more precise statement.
+\end{quote}
 
 P3 L-11 What is an action algebra? I believe it is an undefined term in the paper.
+\begin{quote}
+We have improved the paragraph defining term algebras to identify more precisely the action algebra.
+\end{quote}
 
 P4 L-6 *We distinguish two kinds….* please rewrite this sentence
-
-P4 L1 We additionally *impose*
-
-P4 L6 *negociation* typo
+\begin{quote}
+Done
+\end{quote}
 
 P4 L20 A minor point: Technically, $a^{i\in 3}$ is not allowed by your syntax since indices need to also appear as a subscript.
+\begin{quote}
+\TODO{on a oublie celui-la... ?}
+\end{quote}
 
 P4 L22 I am afraid we do not use abusive vocabulary in mathematics, rather we only abuse notation. Please rewrite.
+\begin{quote}
+Done
+\end{quote}
 
@@
 Donald Knuth on mathematical writing available from $https://jmlr.csail.mit.edu/reviewing-papers/knuth_mathematical_writing.pdf$).
+\begin{quote}
+Done
+\end{quote}
 
 P4 L-9 *We denote y <- e a substitution* What do you mean by this? Do you mean that y<-e is a partial function from the set of variables to terms that is only defined for the variable y as the term e?
+\begin{quote}
+This paragraph has been fully rewritten, giving a more formal definition of substitutions.
+
+This includes answer to this comment and the following three. 
+\end{quote}
 
@@
 
-P4 L-2 Missing comma
-
 P5 Def 1 Is vars(s) defined earlier?
+\begin{quote}
+Yes, in the Notations section, term algebra paragraph.
+\end{quote}
 
 P5 Def 2 How is the symbol $l$ quantified in the clause pertaining to synchronisation vectors.
+\begin{quote}
+This comes from the definition of indexed sets in section 2.1: the superscript $l\in I_k\uplus J_k$ means $l$ as ranging through the set $I_k\uplus J_k$
+\end{quote}
 
 P6 Def 3 In the first clause defining Sort, the notation *?x <- x* is not defined since, technically, a substitution substitutes a variable not a term like ?x.
-
-P6 Def 3 In the third item, *indexes* should be *indices*
+\begin{quote}
+Refering to the Action Algabra definition in section 2.1, the token "?x" is indeed a variable (an input variable).
+\end{quote}
 
 P6 L-15 It would be nice to have a sentence motivating synchronisation vectors that they are essentially transitions; here the example from 2.3 was helpful.
+\begin{quote}
+We have added 2 sentences and a reference, it should help understanding. 
+\end{quote}
 
 P6 Def 4 When is a pNet of the right sort?
+\begin{quote}
+The sorts of pNets and Holes are sets of action signatures, so compatibility is simply set inclusion. We have modified Definition 3.
+\end{quote}
 
 P9 Def 5 Here, is $Sort_j$ again a set of parameterised actions?
+\begin{quote}
+No, Sorts are sets of action signatures. There was a bug here, we have corrected the sort compatibility as "$\Sortop(\beta_j)\in\Sort_j$"
+\end{quote}
 
 P9 Def 5 L6 *all variables in the different terms $\beta_j$ and $\alpha$* What do you mean by this phrase?
+\begin{quote}
+We rewrote this in a more formal way.
+\end{quote}
 
 P9 Def 5 L7 By *assignments* do you mean indexed substitutions?
+\begin{quote}
+We rewrote this in a more formal way.
+\end{quote}
 
@@
 P11 L-8 What do you mean by a finite predicate?
+\begin{quote}
+This was a mistake steaming from an earlier version. We removed "the predicate" from this sentence.
+\end{quote}
 
 P12 L6 Could you expand on what is bisimulation theory for open pNets?
+\begin{quote}
+This was quite a loose formulation. We have rewritten this as "the characterization and properties of a bisimulation relation".
+\end{quote}
 
 P13 Def 9 Please exemplify *I\_1 for the others*?
+\begin{quote}
+We made this more explicit: I1 refers to the set of sub-nets that are not pLTS.
+\end{quote}
 

### 2021-10-10 2016-Weak-FH-Bisim/WeakBisim.tex
Fini la "Letter to reviwers, et ajoute quelques changements mineurs dans le papier
Il reste 2 TODO dans la lettre, et j'ai un Pb sur la cherence des definitions/usages de Sort, 2 TODO dans le papier.

@@
 Formally, we assume the existence of a term algebra $\AlgT$,
-where $\Sigma$ is the signature of the data and action constructors. Within $\AlgT$, we distinguish a set of
- expressions $\AlgE$, including a set of boolean
+and denote as $\Sigma$ the signature of the data and action constructors. Within $\AlgT$, we distinguish a set of
+data expressions $\AlgE$, including a set of boolean
 expressions $\AlgE$ ($\AlgB\subseteq\AlgE$). 
-On top of $\AlgE$ we build the action algebra
+and a set of action expressions $\AlgE$ called the action algebra
 $\AlgA$, with $\AlgA\subseteq\AlgT,
@@
 naturally action terms will use data expressions as sub-terms.
-The function
-$\vars(t)$ identifies the set of variables in a term
+The function $\vars(t)$ identifies the set of variables in a term
 $t\in\AlgT$.
@@
 input variables and we remove the
-\emph{input marker} (?) of variables.
+\emph{input marker} (?) of variables.\TODO{??? ceci ne se retrouve pas dans la def ci-dessous, c'est une vieille version ?}
 \[
@@
 In practice, it is sufficient to check the equality of the two sets of action signatures of the two sorts\footnote{A more complex compatibility relation could be defined, but this is out of the scope of this article.}.
+\TODO{Eric: j'ai 2 pbs ici, d'une part, on ne l'utilise que dans la composition de pNet ci-dessous, ou il nous faudrait plutot l'inclusion des sorts, que l'egalite.
+D'autre part on la definie (Definition 3) comme un ensemble de signatures, mais on cite a plusieurs endroits comme un ensemble d'actions parametrees...
+}
 \end{definition}
@@
 The actions on the \pLTS s can send or receive values, potentially modifying the value of variables.
-pNets are synchronisation entities: a pNet composes several sub-pNets and  synchronisation vectors define how the sub-pNets interact, where a sub-pNet is either a pNet or a pLTS.
-Synchronisation between sub-pNets is defined by synchronisation vectors that express how an action of a sub-pNet can be synchronised with actions of other sub-pNet, and how the resulting synchronised action is visible to the outside of the pNet.
-Consider for example a pNet that assembles several pLTSs, the synchronisation vectors express transitions of the composing pNet: each vector expresses not only the actions emitted by the pNet but also what transitions of the composed pLTSs must occur to trigger this global transition.
+pNets are synchronisation entities: a pNet node composes several sub-pNets and  define how the sub-pNets interact, where a sub-pNet is either a pNet or a pLTS.
+The synchronisation between sub-pNets is defined by synchronisation vectors (originaly introduced by \cite{Arnold1982}) that express how an action of a sub-pNet can be synchronised with actions of other sub-pNet, and how the resulting synchronised action is visible from outside of the pNet.
+The synchronisation mechanism is very expressive, including pattern-matching/unification between the parameterized actions within the vector, and an additional predicate over their variables.
+Consider a pNet node that assembles several pLTSs, the synchronisation vectors specify the way that transitions of the composed pNet are built from the transitions of the sub-nets.
+This can be seen as "conditional transtions" of the pNet, or alternatively, as a syntax to encode structural operational semantics (SOS rules) of the system: each vector expresses not only the actions emitted by the pNet but also what transitions of the composed pLTSs must occur to trigger this global transition.
 Synchronisation vectors can also express the exportation of an action of a sub-pNet to the next level, or to hide an interaction and make it non-observable.
@@
  can be (partially) filled by providing  a pNet $\pNetQ$ to fill one of  its holes.	
-	Suppose $j_0\in J$ and $\Sortop(\pNetQ)$ and $\Sort_{j_0}$ are compatible:
+	Suppose $j_0\in J$ and \ERIC{$\Sortop(\pNetQ) \subset \Sort_{j_0}$}, then: % are compatible:
 	%% \[\mylangle \pNet_i^{i\in I},S_j^{j\in J}, \symb{SV}_k^{k\in
@@
 	Where $J'\subseteq J$ is the set of holes involved in the transition; $s, s'\in\mathcal{S}$ are states of the automaton; and $\beta_j$
-        is a transition of the hole $j$, with $\Sortop(\beta_j)\in\Sort_j$. $\alpha$  is an action 
-        label denoting the resulting action of this open transition.
+        is a transition of the hole $j$, with $\Sortop(\beta_j)\in\Sort_j$. $\alpha$  is the resulting action of this open transition.
 %        We call \emph{source variables} of an OT the union of all variables

### 2021-10-12 2016-Weak-FH-Bisim/2021-09-letter2Reviewers.tex

@@
 \begin{itemize}
-\item 
+\item revised introduction: added expklanations on the two formalisms and why both are useful in the context of this article; also better exlained the characteristics of oa bisim, the nature of our formalisms, and the novelty of the results
+\item We refined and improved the formalisation of several aspects: substitution, sorts,  and unified some notations (e.g. use of indices in the relations.)
+\item In particular, we improved and specified correctly the nature of the bisimulation relation (FH-bisimulation), its signature, and the impact of the symbolic nature of the relation.
+\item We added an example illustrating the difference between our bisimulation and weak bisimulation for CS (more specifically for a process algebra with a choice operator and a $\tau$ action)
+\item We improved related works with a positioning relatively to ``negative premisses'' and ``conditional transitions''.
 \end{itemize}

### 2021-10-12 2021-Refinement/paper/refinementarticle.tex

@@
 \AtBeginDocument{\renewcommand\setminus{\smallsetminus}}
+
+\DeclareMathOperator{\dom}{dom}
 
@@
 
-This section presents the notations we used and the principles of automata.
-Except for minor changes in the notations, the only new contribution of this section is the definition of a composition operator for open automata.
+This section presents our notations and the principles of automata.
+Except for minor changes in the notations, compared to previous works~\cite{pnets} the only new contribution is the definition of a composition operator for open automata.
 %
@@
 \( E=\terms \uplus \actions \uplus \formulas\) .
-\(\terms\) and \(\actions\) are term algebras.
+\(\terms\) and \(\actions\) are term algebras \TODO{do we explain term algebras}.
 The formulas \(\formulas\) contain at least first order formulas and equality\footnote{Equality does not need to be only syntactic.} over \(\terms\) and \(\actions\). 
@@
 \item The satisfiability of a formula \(f \in \formulas\) under some valuation \(\sigma: V \to \values\) is defined as follows:
-\( \sigma \vdash f ::= \vdash \exists \fvars{f\psubst{\sigma}}, f\psubst{\sigma} \)
+\( \sigma \vdash f \iff \vdash \exists \fvars{f\psubst{\sigma}}, f\psubst{\sigma} \)
 \item The satisfiability of a formula \(f \in \formulas\) with some variable set \(V\) as context is defined as follows:
-\( V \vdash f ::=  \vdash \forall V, \exists\mpar{\fvars{f} \setminus V}, f \)
+\( V \vdash f \iff  \vdash \forall V, \exists\mpar{\fvars{f} \setminus V}, f \)
 \end{itemize}
@@
 
-The following terminology will be used to reason on open automata
-\begin{definition}[Configuration, instantiated transition]
-A pair of a state and a valuation is called a \emph{configuration}.
-An \emph{instantiated transition} of an automaton \(\OAg\) is a transition  \(t\psi\) where $t\in T$ and $\psi$ is a  well-formed substitution of the unbound variables of $t$  minus the automaton variables $V$.
-\end{definition}
-
-\TODO{useful or not?}
+%\TODO{useful or not?}
 \begin{definition}[Guard, Out-transition, Transition variables]
@@
 \begin{align*}
-	\fOT[T]{r} & ::= \mset{\OTg \in T}{s = r} &
-	\fIT[T]{r} & ::= \mset{\OTg \in T}{s' = r} \\
+	\fOT[T]{r} & = \mset{\OTg \in T}{s = r} &
+	\fIT[T]{r} & = \mset{\OTg \in T}{s' = r} \\
 \end{align*}
@@
 \begin{gather*}
-	\fguard{\OTg} ::= g \\
-	\fvars{\OTg} ::= \mpar{\fvars{\alpha} \cup \fvars{g} \cup \bigcup_{j \in J'} \fvars{\beta_j} \cup \bigcup_{v \in V} \fvars{\psi\mpar{v}}} \setminus V
+	\fguard{\OTg} = g \\
+	\fvars{\OTg} = \mpar{\fvars{\alpha} \cup \fvars{g} \cup \bigcup_{j \in J'} \fvars{\beta_j} \cup \bigcup_{v \in V} \fvars{\psi\mpar{v}}} \setminus V
 \end{gather*}
+\end{definition}
+
+The following terminology will be used to reason on open automata
+\begin{definition}[Configuration, instantiated transition]
+A pair consisting of a state and a valuation is called a \emph{configuration}.
+An \emph{instantiated transition} of an automaton \(\OAg\) is a transition  \(t\psi\) where $t\in T$ and $\psi$ is a  well-formed substitution with $\dom(\psi)=vars(t)$. %\setminus V$.
 \end{definition}
@@
 The definition of composition below is a direct translation of what happens with pNets composition without the need of introducing pNets.
+
+\TODO{peut etre echanger c et p? ou c devient p et p devient? }
 \begin{definition}[Composition of open automata]
@@
 As an example, the traffic light system  that controls  
- traffic at the intersection of a busy highway. The open automaton  
+ traffic at an intersection. The open automaton  
 modeling this system  is illustrated in  Figure \ref{fig:tls}. This automaton has three states  remembering which coloured light
@@
 
-\begin{figure}
+\begin{figure}[!tb]
 \centering
-\input{Traffic_Lights_Spec.tex}
+\scalebox{.75}{\input{Traffic_Lights_Spec.tex}}
 \caption{The specification of a Traffic Light system}
@@
 
-\begin{figure}
+\begin{figure}[!tb]
 %\centering
-\input{Traffic_Lights_Controller.tex}
-\input{Traffic_Lights_Register.tex}
+\scalebox{.75}{\input{Traffic_Lights_Controller.tex}}
+\scalebox{.75}{\input{Traffic_Lights_Register.tex}}
 \caption{(a) An example of controller component ~~  (b) An example of counter component}
@@
 
-\begin{figure}
+\begin{figure}[!tb]
 \centering
-\input{Traffic_Lights_Interm.tex}
+\scalebox{.75}{\input{Traffic_Lights_Interm.tex}}
 \caption{The incomplete Specification Traffic Lights system}
@@
 
-\begin{figure}
+\begin{figure}[!tb]
 \centering
-\input{Traffic_Lights_Full.tex}
+\scalebox{.75}{\input{Traffic_Lights_Full.tex}}
 \caption{The full Traffic Lights system}
@@
 
-Similarly to FH-bisimulation~\cite{fhbisim} we are interested here in finding relations between states of to open automata that contain variables and holes.
-However here we want to build a refinement relation that is a simulation but also guarantees that no deadlock is introduced.
-Our objective is to characterize when a relation between two states of two open automata have the desired property.
-Such a relation has the following signature: \( S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
-We first define when a relations is deadlock reducing, before characterising a first simple refinement relation only valid to compare automata with identical holes.
+Similarly to FH-bisimulation~\cite{fhbisim} we are interested  in finding relations between states of to open automata that contain variables and holes.
+However here we want to build a refinement relation that  also guarantees that no deadlock is introduced when refining the automaton.
+The refinement relation should be conditioned by the internal states of the automata.
+More precisely, a refinement relation characterizes when two states are related, this  characterisation is expressed as a predicate on the variables of the two automata.
+Thus, a refinement relation has the following signature: \( S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
+
+\TODO{check deadlock reduction/reducing in the literature}
+We first define when a relation is deadlock reducing, before characterising a first simple refinement relation  to compare automata with identical holes.
 
 \subsection{Deadlock Reduction, Reachability, and Composition}
+
+\TODO{commmenter avec}
+
+perhaps say that one of the automaton is expected to be the reinement of the other BUT the def is not dependent on the notion of refinement
+
+Beware implicit existential quantification on vars of t1
+
+Next definition is not intuitive, it does not say much because it says that if t2 is not in a deldlock position then t1 can do a transition but not necessarily with the same input values.
+This is very weak but sufficient when composed with the def  of simulation.
 
@@
 This second definition is more complex, in particular because of the multiple quantifiers over transitions and automaton state.
+The alternative definition is equivalent to this one when reasoning on a refinement relation (but not in general).
 
@@
 \begin{definition}[Reachability]
-For any open automata \(A = \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is any predicate on states that is preserved across transitions, and valid on initial state:
+For any open automata \(A = \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is any predicate on states that is valid on initial state, and preserved across transitions:
 \[\sigma_0 \vdash \reach{A}\mpar{s_0}\quad\land\quad\forall t = \OTg \in T, \fvars{t} \vdash \left(\reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}\right)\]
 \end{definition}
-Reachability takes into account all paths, and potentially over-approximate the reachable configurations and must be representable as a formula.
+Reachability takes into account all paths, and can over-approximate the reachable configurations. 
+\TODO{rediger la phrase suivante}
+Because of the over approximation, to implement a verifier it is possible to try find a formula that over-approximate the reachability property and is representable in the tool.
 % LUDO HERE
 \begin{definition}[Non-locking composition]
-Let \(A_i = \OAg[i], 0 \leq i \leq n\).
-The composition \(A = A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) 
- is a non-locking composition if if \(A \) has a reachability predicate satisfying the following.
-From reachable configurations, if there was a possible transition in \(A_0\) then there is a possible transition in \(A\):
-\[ \forall s = \mpar{s_0, s'} \in S, V \uplus \biguplus_\subbox{t_0 \in \fOT{s_0}} \fvars{t_0} \vdash \left(\reach{A}\mpar{s} \wedge \bigvee_\subbox{t_0 \in \fOT{s_0}} \fguard{t_0} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \right)\]
+Let \(A_i = \OAg[i]\) with \( 0 \leq i \leq n\) be a family of open automata.
+Let \(A = A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) and $A= \OAg$.
+
+The composition \(A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is non-locking if   \(A \) has a reachability predicate such that, for each reachable configuration, if there is a possible transition in \(A_0\) then there is a possible transition in \(A\):
+\[ \forall s = \mpar{s_0, s_1,..,s_n} \in S, V \uplus \biguplus_\subbox{t_0 \in \fOT{s_0}} \fvars{t_0} \vdash \left(\reach{A}\mpar{s} \wedge \bigvee_\subbox{t_0 \in \fOT{s_0}} \fguard{t_0} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \right)\]
 \end{definition}
-Again we use guards as a characteristics that the transition occurs.
+Again we use guards to characterise that the transition occurs.
+It is not sufficient to ensure the existence of equivalent transitions in general, but it will be sufficient in the context of refinement.
 

### 2021-10-12 2016-Weak-FH-Bisim/2021-09-letter2Reviewers.tex
bullet in letter 2 reviewers

--- 2021-10-10 2016-Weak-FH-Bisim/2021-09-letter2Reviewers.tex
@@
   addressed trivially and exactly as suggested by the reviewers are
-  omitted}.  \bigskip
+  omitted}.  \medskip
 
@@
 \begin{itemize}
-\item 
+\item We revised the introduction with explanations on the two formalisms and why both are useful in the context of this article; we also better explained the characteristics of FH-bisimulation, and the nature of our formalisms.
+We also better highlight the novelty of the results.
+
+To summarise, in order to equip  pNets with a bisimulation relation we need to define transitions that takes holes into account and are symbolic.
+This is exactly the characteristics of open transitions (and open automata).
+\item We refined and improved the formalisation of several aspects: substitution, sorts. We also unified some notations (e.g. use of indices in the relations).
+
+ In particular, we improved and specified correctly the nature of the bisimulation relation (FH-bisimulation), its signature, and the impact of the symbolic nature of the relation.
+
+\item We added an example illustrating the difference between our weak bisimulation and weak bisimulation for CCS (more specifically for a process algebra with a choice operator and a $\tau$ action)
+
+\item We improved related works with a positioning relatively to ``negative premisses'' and ``conditional transitions''.
+
+\item The last section has also been extended with a discussion on refinement checking and on tool support.
 \end{itemize}

### 2021-10-12 2016-Weak-FH-Bisim/WeakBisim.tex
choice and major points in letter
bullet in letter 2 reviewers

@@
 perform, where each action signature is an action 
-label plus the arity of the action. In the definition of sorts, we do not need to 
-distinguish
-input variables and we remove the
-\emph{input marker} (?) of variables.\TODO{??? ceci ne se retrouve pas dans la def ci-dessous, c'est une vieille version ?}
+label plus the arity of the action.
+% Note that, in this definition of sorts we do not  
+%distinguish
+%input variables from other expressions.
+%and only  and we remove the
+%\emph{input marker} (?) of variables.\TODO{??? ceci ne se retrouve pas dans la def ci-dessous, c'est une vieille version ?}
 \[
@@
 In practice, it is sufficient to check the equality of the two sets of action signatures of the two sorts\footnote{A more complex compatibility relation could be defined, but this is out of the scope of this article.}.
-\TODO{Eric: j'ai 2 pbs ici, d'une part, on ne l'utilise que dans la composition de pNet ci-dessous, ou il nous faudrait plutot l'inclusion des sorts, que l'egalite.
+%\TODO{Eric: j'ai 2 pbs ici, d'une part, on ne l'utilise que dans la composition de pNet ci-dessous, ou il nous faudrait plutot l'inclusion des sorts, que l'egalite.
 D'autre part on la definie (Definition 3) comme un ensemble de signatures, mais on cite a plusieurs endroits comme un ensemble d'actions parametrees...
@@
  can be (partially) filled by providing  a pNet $\pNetQ$ to fill one of  its holes.	
-	Suppose $j_0\in J$ and \ERIC{$\Sortop(\pNetQ) \subset \Sort_{j_0}$}, then: % are compatible:
+	Suppose $j_0\in J$ and \ERIC{$\Sortop(\pNetQ) \subseteq \Sort_{j_0}$}, then: % are compatible:
 	%% \[\mylangle \pNet_i^{i\in I},S_j^{j\in J}, \symb{SV}_k^{k\in
@@
 Here is the encoding of a choice operator.\\[1.5ex]
-\begin{tabular}{cp{.52\linewidth}}
- \begin{minipage}{.46\linewidth}
+\begin{tabular}{cp{.53\linewidth}}
+ \begin{minipage}{.43\linewidth}
  \includegraphics[width=\linewidth]{XFIG/Choice.pdf}\vspace{-18ex}

### 2021-10-12 2016-Weak-FH-Bisim/WeakBisim.tex
subseteq

@@
 	weak bisimilarity.} 
-	$\Sortop(\pNetQ)=\Sortop(\pNetQ')=\Sort_{j_0}$. Then 
+	$\Sortop(\pNetQ)=\Sortop(\pNetQ')\subseteq\Sort_{j_0}$. Then 
 	$\pNet[\pNetQ]_{j_0}$ and 
@@
 	(recall they must have the same holes to be bisimilar) and that cannot observe silent actions.
-	Let $j_0\in J$ be a hole, and $\pNetQ$ be a pNet such that $\Sortop(\pNetQ)=\Sort_{j_0}$. Then 
+	Let $j_0\in J$ be a hole, and $\pNetQ$ be a pNet such that $\Sortop(\pNetQ)\subseteq\Sort_{j_0}$. Then 
 	$\pNet[\pNetQ]_{j_0}$ and 
@@
 	Let $j_0\in J$ be a hole. Let $\pNetQ$ and $\pNetQ'$ be two FH-bisimilar pNets such that 
-	$\Sortop(\pNetQ)=\Sortop(\pNetQ')=\Sort_{j_0}$\footnote{Note that $\Sortop(\pNetQ)=\Sortop(\pNetQ')$ is 
+	$\Sortop(\pNetQ)=\Sortop(\pNetQ')\subseteq\Sort_{j_0}$\footnote{Note that $\Sortop(\pNetQ)=\Sortop(\pNetQ')$ is 
 	ensured by 
@@
 	(recall they must have the same holes to be bisimilar).
-	Let $j_0\in J$ be a hole, and $Q$ be a pNet such that $\Sortop(Q)=\Sort_{j_0}$. Then 
+	Let $j_0\in J$ be a hole, and $Q$ be a pNet such that $\Sortop(Q)\subseteq\Sort_{j_0}$. Then 
 	$\pNet[Q]_{j_0}$ and 

### 2021-10-13 2016-Weak-FH-Bisim/WeakBisim.tex
t_i to solve problem

@@
 family is indexed, and then $t_i$ the elements of the family.
-For example $t^{i\in\{3\}}$ is
-the mapping with a single entry $t$ at index $3$; exceptionally, for mappings with
-only a few entries we use the notation $(3\mapsto t)$ instead.
+For example $t_i^{i\in\{3\}}$ is
+the mapping with a single entry $t_3$ at index $3$; exceptionally, for mappings with
+only a few entries we use the notation $(3\mapsto t_3)$ instead.
 In this article, sentences of the form ``there exists $t_i^{i\in I}$'' means there exists $I$ and a function that maps each element of $I$ to a term $t_i$.

### 2021-10-13 2016-Weak-FH-Bisim/2021-09-letter2Reviewers.tex
t_i to solve problem
letter: sentence on choice and weak bisim

@@
 Indeed, the plus operator of CCS does not verify the requirements ``non-observability of tau transitions'' for the weak bisimulation to be a congruence. 
-We can define the weak bisimulation for CCS but it does not verify the congruence property.
-\TODO{define the bisimulation, or encode the nondeterministic choice operator ?}
+We can encode a choice operator for CCS and derive the weak bisimulation for processes with this operator, 
+but this weak bisimulation does not verify the requirements for the congruence property.
+This is consistent with the fact that weak bisimulation is not a congruence for CCS, and our formalism allows us to explain why.
 
-This is now illustrated by Example 4 and 5 in the article.
+This is now explained and illustrated by Example 4 and 5 in the article.
 \end{quote}
@@
 Done
-\end{quote}
-
-P4 L20 A minor point: Technically, $a^{i\in 3}$ is not allowed by your syntax since indices need to also appear as a subscript.
-\begin{quote}
-\TODO{on a oublie celui-la... ?}
 \end{quote}

### 2021-10-13 2016-Weak-FH-Bisim/WeakBisim.tex
one more pass in the train

@@
 predicates on the transitions are obtained both from the predicates on
-the pLTSs transitions and from the synchronisation vectors involved in
+the transitions of the pLTSs, and from the synchronisation vectors involved in
 the transition.
@@
 \subsection{Deriving an open automaton from an open pNet}
-To derive an open automaton from a pNet, we need to describe the set of states of the automaton, and then we will detail the construction rule for transitions of the automaton, this will rely on the derivation of predicates unifying synchronisation vectors and the actions of the pNets involved in a given synchronisation.
+To derive an open automaton from a pNet, we first describe the set of states of the automaton.
+Then we show the construction rule for transitions of the automaton, this  relies on the derivation of predicates unifying synchronisation vectors and the actions of the pNets involved in a given synchronisation.
 
@@
 
-We first define states of open pNets as tuples of states. We denote them
+States of open pNets are tuples of states. We denote them
  as $\triangleleft\ldots\triangleright$ for distinguishing tuple 
@@
 To be precise, the state of each pLTS is entirely characterized by both the state of the automaton, and the value of its variables $V$.
-Consequently, the complete characterization of the state of a pNet should take into account the value of its variables $vars(P)$.
+Consequently, the state of a pNet is not only characterized the tuple of pLTS states but also contains the value of its variables $vars(P)$.
 
@@
 	\Holes(\pNet)$, $I_2=M\cap \Leaves(\pNet)$,  $I_1=M\setminus J \setminus 
-	I_2$}\footnote{It is of course possible to replace $I_1$ and $I_2$ by their formal definition in \textbf{Tr2} but the rule would be more difficult to read.}.
+	I_2$}\footnote{We could replace $I_1$ and $I_2$ by their formal definition in \textbf{Tr2} but the rule would be more difficult to read.}.
 \begin{mathpar}

### 2021-10-18 2016-Weak-FH-Bisim/WeakBisim.tex
correct mineures

@@
 
-pNets is a generalisation of automata that model open systems.
+pNet is a generalisation of automata that model open systems.
 They feature variables and hierarchical composition.
@@
 \subsubsection*{pNets and open automata}
-pNets is a convenient model to model concurrent systems in a hierarchical and parameterised way.
+pNet is a convenient model to model concurrent systems in a hierarchical and parameterised way.
 The coordination between processes is expressed as synchronisation vectors that allow the definition of complex and expressive synchronisation patterns.
@@
 Compositionality of bisimulation in our model come from the specification of the interactions, including actions of the holes.
-In pNets synchronisation vectors define the possible interactions between the pNet that fills the hole and the surrounding pNets.
+In pNets, synchronisation vectors define the possible interactions between the pNet that fills the hole and the surrounding pNets.
 In open automata, this is reflected by symbolic hypotheses that depend on the actions of the holes.
@@
 data expressions $\AlgE$, including a set of boolean
-expressions $\AlgE$ ($\AlgB\subseteq\AlgE$). 
+expressions $\AlgE$ ($\AlgB\subseteq\AlgE$), 
 and a set of action expressions $\AlgE$ called the action algebra
@@
 pNets are synchronisation entities: a pNet node composes several sub-pNets and  define how the sub-pNets interact, where a sub-pNet is either a pNet or a pLTS.
-The synchronisation between sub-pNets is defined by synchronisation vectors (originaly introduced by \cite{Arnold1982}) that express how an action of a sub-pNet can be synchronised with actions of other sub-pNet, and how the resulting synchronised action is visible from outside of the pNet.
+The synchronisation between sub-pNets is defined by synchronisation vectors (originally introduced by \cite{Arnold1982}) that express how an action of a sub-pNet can be synchronised with actions of other sub-pNet, and how the resulting synchronised action is visible from outside of the pNet.
 The synchronisation mechanism is very expressive, including pattern-matching/unification between the parameterized actions within the vector, and an additional predicate over their variables.
@@
  can be (partially) filled by providing  a pNet $\pNetQ$ to fill one of  its holes.	
-	Suppose $j_0\in J$ and \ERIC{$\Sortop(\pNetQ) \subseteq \Sort_{j_0}$}, then: % are compatible:
+	Suppose $j_0\in J$ and $\Sortop(\pNetQ) \subseteq \Sort_{j_0}$, then: % are compatible:
 	%% \[\mylangle \pNet_i^{i\in I},S_j^{j\in J}, \symb{SV}_k^{k\in
@@
 
-Figure \ref{SimpleProt:Impl} shows the pNet model of the protocol implementation, called $\symb{SimpleProtocolImpl}$ .
+Figure \ref{SimpleProt:Impl} shows the pNet model of the protocol implementation, called $\symb{SimpleProtocolImpl}$.
 When the $\symb{Medium}$ detects an error (modelled by a local $\tau$ action), it sends back a $\texttt{m-error}$ message to the $\symb{Sender}$.
@@
 The assignments are always applied simultaneously because the variables in $V$ can be in both sides ($x_k$s are distinct).
-
+\TODO{$\forall k.\, x_k\in V \land \vars(e_k)$ pas clair!? c'est plutot cap?}
  Open transitions are identified
@@
 We define now a bisimulation relation tailored to open automata and their parametric nature.
-This relation relates states of the open automaton and guarantees that the related states are observationally equivalent, i.e.
+This relation relates states of the open automata and guarantees that the related states are observationally equivalent, i.e.
 equivalent states can trigger transitions with identical action labels.
@@
 
-\begin{example}[CCS Choice] Consider the $+$ operator of CCS,shown in  Example~\ref{ex:CCSplus}.
+\begin{example}[CCS Choice] Consider the $+$ operator of CCS, shown in  Example~\ref{ex:CCSplus}.
 It is well-known that weak bisimulation is not a congruence in CCS, and this is reflected here because we have shown that the $+$ operator can observe the $\tau$ transitions.
-Thus, even if we can define a weak bisimulation for CCS with $+$ it does verify the necessary requirements for being a congruence.
+Thus, even if we can define a weak bisimulation for CCS with $+$ it does not verify the necessary requirements for being a congruence.
 \end{example}

### 2021-10-19 2016-Weak-FH-Bisim/2021-09-letter2Reviewers.tex
one more pass in the train
small typo/style fixing.

@@
 
-\item We added an example illustrating the difference between our weak bisimulation and weak bisimulation for CCS (more specifically for a process algebra with a choice operator and a $\tau$ action)
+\item We added an example illustrating the difference between our weak bisimulation and weak bisimulation for CCS (more generaly for a process algebra with a choice operator and a $\tau$ action)
 
-\item We improved related works with a positioning relatively to ``negative premisses'' and ``conditional transitions''.
+\item We improved explanations wherever the reviewers indicated it was necessary (e.g.  semantics of pNets,  definition of bisimulation, definition of weak open transitions)
+
+\item We improved related works with a positioning with respect to ``negative premisses'' and ``conditional transitions''.
 
@@
 \begin{quote}
-The definition of pNets is indeed not simple but as it is placed at a very generic and semantic leve,l we do not believe there are good alternatives in the literature.
+The definition of pNets is indeed not simple but as it is placed at a very generic and semantic level, we do not believe there are good alternatives in the literature.
 Process algebras for example do not feature the hierarchical and parametric aspects of pNets and defining equivalence checking tools on these frameworks is difficult.
-Of course the examples can be expressed in any concurrent Turing-complete model but none of the existing works feature the same results as ours on the modelling of existing parallel operators, and compositional reasoning on equivalence.
+Of course the examples can be expressed in any concurrent Turing-complete model but none of the existing works feature the same results as ours on the modelling of classical parallel operators, and compositional reasoning on equivalence.
 
@@
 \begin{quote}
-The reason for the coexistence of the two formalisms is that one is hierarchical and adapted to modelling, the other is flat and more based on logic, and adapted to semantic/equivalence reasoning.
+The reason for the coexistence of the two formalisms is that one is hierarchical and adapted to the modelling of high level languages, the other is flat and more based on logic, and adapted to semantic/equivalence reasoning.
 We added one subsection in the introduction that presents the two formalisms and the reason why both exist.
@@
 \begin{quote}
-$\otimes$ is a form of composition: we have changed for something similar to $\circ$, renamed it into $\odot$
+$\otimes$ is a form of composition: we have changed for something similar to the functional composition symbol $\circ$, renamed it into $\odot$
 \end{quote}
@@
 \begin{quote}
-In the context of this article, we consider that an indexed set $OT_x^{x\in X}$ defines both an indexation set $X$ and a set of elements $OT_x$ for $x\in $.
+In the context of this article, we consider that an indexed set $OT_x^{x\in X}$ defines both an indexation set $X$ and a set of elements $OT_x$ for $x\in X$.
 We additionally clarified this in the notation section.

### 2021-10-20 2016-Weak-FH-Bisim/WeakBisim.tex
TODOs

@@
         $\beta_j$ and $\alpha$. More precisely:
-\[ \vars(\Pred) \subseteq V\cup\vars(\alpha)\cup
-			{\displaystyle \bigcup_{j\in J'}\!\!\vars(\beta_j)}\quad\land\quad
-\forall k.\, x_k\in V \land \vars(e_k)\subseteq V\cup\vars(\alpha)\cup
-			{\displaystyle \bigcup_{j\in J'}\!\!\vars(\beta_j)}\]
-The assignments are always applied simultaneously because the variables in $V$ can be in both sides ($x_k$s are distinct).
-\TODO{$\forall k.\, x_k\in V \land \vars(e_k)$ pas clair!? c'est plutot cap?}
+\begin{multline*}
+ \vars(\Pred) \subseteq V\cup\vars(\alpha)\cup
+			{\displaystyle \bigcup_{j\in J'}\!\!\vars(\beta_j)}\quad\land\\
+\forall k.\, x_k\in V \quad\land\quad \forall k.\,\vars(e_k)\subseteq V\cup\vars(\alpha)\cup
+			{\displaystyle \bigcup_{j\in J'}\!\!\vars(\beta_j)}
+\end{multline*}
+The assignments are applied simultaneously because the variables in $V$ can be in both sides ($x_k$s are distinct).
  Open transitions are identified
@@
 
-For all predicate $\Pred$, for all partial functions $\Post$ such that $V\cap \dom(\Post)=\emptyset$. We have: 
+For all predicate $\Pred$ for all partial function $\Post$,if $V\!\cap \!\dom(\Post)=\emptyset$, we have: 
 		 \begin{mathpar}
@@
 
-Though the definition is simple, the fact that transitions are complex structures relating events must not be underestimated in order to understand the rest of the article.
+Though the definition is simple, the fact that transitions are complex structures relating events must not be underestimated.
 The first element of theory for open automata, i.e.
@@
  \mathcal{R}$
- and  \\
- $\Pred_{s,t} \land \Pred_{OT}\implies$\\
+ and  
+\begin{multline*}
+ \Pred_{s,t} \land \Pred_{OT}\implies\\
 %\hspace{1cm}
- $\displaystyle{\bigvee_{x\in X}
+ \displaystyle{\bigvee_{x\in X}
    \left( \forall j. \beta_j=\beta_{jx}  \land \Pred_{OT_x}
      \land \alpha\!=\!\alpha_x \land  
-     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}$
+     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}
+\end{multline*}
      %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
@@
 \label{Appendix:FullExample}
-\TODO{Ludo: spec implem dans l annexe}
 

### 2021-10-20 2016-Weak-FH-Bisim/WeakBisim.tex
mise en page de formules

@@
  This predicate verifies:
-\[\begin{array}{l}\Predsv \Big(\left(\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
+\begin{multline*}
+\Predsv \Big(\left(\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
 {\alpha'} 
@@
 \land e_b
-\end{array} 
-%\bigg)
-\]
+\end{multline*}
 
@@
  such that  $\forall x.\, \{j\in J'|\beta_j\neq\tau\}=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
- and  \\
- $\Pred_{s,t} \land \Pred_{OT}\\
+ and  
+\begin{multline*}
+\Pred_{s,t} \land \Pred_{OT}\\
 \hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
@@
      \!\land\! \alpha\!=\!\alpha_x\! \land\!  
-     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}$
+     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}
+\end{multline*}
 
@@
        	\mathcal{R}$;
-       	and  \\
-
-       	$\Pred_{s,p} \land \Pred_{OT}\\
-       	\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}
+       	and  
+\begin{multline*}
+       	\Pred_{s,p} \land \Pred_{OT}\\
+ \implies \bigvee_{x\in X}
        	\left( \forall j. \beta_j=\beta_{jpx}  \land \Pred_{OT_{px}}
        	\land \alpha\!=\!\alpha_{px} \land
-       	\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\right)}$\\
+       	\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\right)
+\end{multline*}
 
@@
        	such that  $\forall y, J_{px}=J_{pxy}, 
-       	(t_{px},u_{pxy}|\Pred_{{pxy}})\in \mathcal{R}'$; and  \\
-       	$\Pred\,'_{p,u} \land \Pred_{OT_{p x}}\\
+       	(t_{px},u_{pxy}|\Pred_{{pxy}})\in \mathcal{R}'$; and  
+\begin{multline*}
+\Pred\,'_{p,u} \land \Pred_{OT_{p x}}\\
        	\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}\!
@@
        	\land\! \alpha_{px}\!=\!\alpha_{pxy} \!\land\!
-       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}\!\uplus\!\Post_{OT_{pxy}}}\right)}$\\
+       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}\!\uplus\!\Post_{OT_{pxy}}}\right)}
+\end{multline*}
 
@@
 $\displaystyle{\Pred_{s,u} \land \Pred_{OT}}\\
- \implies\!\!\! \bigvee_{p\in P} (
+{~}\hspace{1cm}~ \implies\!\!\! \bigvee_{p\in P} (
 	\Pred_{s,p}\land\Pred_{p,u} \land \Pred_{OT})\\
-\hspace{1cm} \implies\!\!\!\bigvee_{p\in P}
+{~}\hspace{1cm}~ \implies\!\!\!\bigvee_{p\in P}
  \bigvee_{x\in X} \bigvee_{y\in Y}
@@
 \land \Pred_{OT_{pxy}}\\
-~\hspace*{2em}~\land \alpha\!=\!\alpha_{px}\!=\!\alpha_{pxy}\land\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus \Post_{OT_{pxy}}}\big)
+~\hspace*{3em}~\land \alpha\!=\!\alpha_{px}\!=\!\alpha_{pxy}\land\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus \Post_{OT_{pxy}}}\big)
 \\
-\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
+{~}\hspace{1cm}~ \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
 \left( \forall j. \beta_j\!=\!\beta_{jpxy}  \land \Pred_{OT_{pxy}}
@@
  \Pred_{s,t}\land\Pred\,'\land \Pred\,''\land \alpha_Q=\beta_{j_0}\\  
- \implies  \hspace{-2ex}
+{~}\hspace{1cm}~ \implies  \hspace{-2ex}
 {\displaystyle{\bigvee_{x\in X}\!(\forall j\!\in\! J'. \beta_j\!=\!\beta_{jx}  
@@
 			%FH for P
- \implies  \hspace{-2ex}
+{~}\hspace{1cm}~ \implies  \hspace{-2ex}
 	{\displaystyle{\bigvee_{x\in X}\!(\forall j\!\in\! J'. \beta_j\!=\!\beta_{jx}  

### 2021-10-20 2016-Weak-FH-Bisim/WeakBisim.tex
small change

--- 2021-10-18 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 			{\displaystyle \bigcup_{j\in J'}\!\!\vars(\beta_j)}\quad\land\quad
-\forall k.\, x_k\in V \land \vars(e_k)\subseteq V\cup\vars(\alpha)\cup
+\forall k.\, x_k\in V \land \vars(e_k) \subseteq V\cup\vars(\alpha)\cup
 			{\displaystyle \bigcup_{j\in J'}\!\!\vars(\beta_j)}\]
 The assignments are always applied simultaneously because the variables in $V$ can be in both sides ($x_k$s are distinct).
-\TODO{$\forall k.\, x_k\in V \land \vars(e_k)$ pas clair!? c'est plutot cap?}
+
  Open transitions are identified

### 2021-10-20 2016-Weak-FH-Bisim/WeakBisim.tex
improved style
typos annexes

--- 2021-10-20 2016-Weak-FH-Bisim/WeakBisim.tex
@@
         $\beta_j$ and $\alpha$. More precisely:
+
 \begin{multline*}
@@
 The assignments are applied simultaneously because the variables in $V$ can be in both sides ($x_k$s are distinct).
+
  Open transitions are identified
@@
  A classical relation between states can be seen as a function mapping pairs of state to a boolean value (true if the states are related, false if they are not).
-A FH-bisimulation relation maps pairs of states to boolean expressions that use variables of the two systems.
+An FH-bisimulation relation maps pairs of states to boolean expressions that use variables of the two systems.
 %Each variable used in $\Pred_{s,t}$ should refer to a state variable of $s$ or $t$ and there must be no ambiguity on the referenced variable, we thus require that the two compared automata have disjoint state variables.
@@
 the action algebra $\AlgA$. Then it is decidable whether the relation 
-$\mathcal{R}$ is a FH-bisimulation.
+$\mathcal{R}$ is an FH-bisimulation.
 
@@
 
-       	There exist open transitions $OT_{p x}^{x\in X} \subseteq \mathcal{T}_2$:
+       	There exists an indexed set of open transitions $OT_{p x}^{x\in X} \subseteq \mathcal{T}_2$:
 
@@
 
-From (*) and (**) we have, for all $p$
+\medskip
+\noindent From (*) and (**) we have:\\ 
+for all $p$,
        	\begin{small}
@@
 Consider first the open transition derived from $P$.
-       Consider each premise of the open transition (constructed by \TrDeux\ in 
+       Consider each premise of the open transition (constructed by \TrDeux\ rule in 
 Definition~\ref{def:operationalSemantics}). 
@@
 	\alpha=\alpha'\land \alpha_Q=\beta_{j_0}\land \beta_{j_0}=\alpha_{j_0}\land e_b$
- and by definition of $\Pred$ (as obtained by \TrDeux),
+ and by definition of $\Pred$ (as obtained by applying \TrDeux~rule),
 	$\Pred\,''\iff \Pred\land\Pred\,'\land \alpha_Q=\beta_{j_0}$. The post-condition 
@@
     		\!\!\!\!\!\Post_m = 	\Post\uplus \Post\,'}$.\\ Finally, the composed open transition can be
-        built by \TrDeux\ as follows:
+        built by \TrDeux\ rule as follows:
 	\noindent
@@
 
-In this section, we first define two alternative definitions, one for weak open transition, one for for weak bisimulation.
+In this section, we first define two alternative definitions, one for weak open transition, one for  weak bisimulation.
 We use these two alternative definitions to show that weak bisimulation is an equivalence, we will also re-use these alternative definitions in the  proofs of the theorems in next sections.
@@
 \noindent ($\Leftarrow$) We proceed by structural induction on the rules  building  the weak transition (as described in the original definition).
-The recurrence hypothesis being that the  the original definition implies the characterization (1), with the conditions stated at the bottom of the theorem.
+The recurrence hypothesis being that the  original definition implies the characterization (1), with the conditions stated at the bottom of the theorem.
 We consider the different rules:
@@
 
-All the combinations of elements in $A$, $B$, and $C$ provides a set $X$ of weak open transitions (each combination of one transition in $A$, one in $B$, and one in $C$ provides one weak open transition in the set $X$, i.e.
+All the combinations of elements in $A$, $B$, and $C$ provide a set $X$ of weak open transitions (each combination of one transition in $A$, one in $B$, and one in $C$ provides one weak open transition in the set $X$, i.e.
 each $x\in X$ corresponds to a triple $(a,b,c)\in A\times B\times C$); this defines a set of weak open transitions indexed over $X$;  each such open transition leads to a $w_c$ that we call $t_x$.
@@
 Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha'_p$ some of them may be non-observable (they are $\tau$ transitions).
-By considering the sequence of $\tau$ and non-$\tau$ actions we split the sequence of actions into $n+1$ sub-sequences, such that each subsequence is a sequence of actions containing  only one observable action that will be named $\alpha_p$, and possibly many non-observable ($\tau$) ones.
+By considering the sequence of $\tau$ and non-$\tau$ actions we split the sequence of actions into $n+1$ sub-sequences, such that each sub-sequence is a sequence of actions containing  only one observable action that will be named $\alpha_p$, and possibly many non-observable ($\tau$) ones.
 
@@
  \begin{proof}  Consider $Q$ weak FH-bisimilar to $Q'$.
-It means that there exist a FH-bisimulation $\mathcal{R}_{Q,Q'}$ relating the two pNets $Q$ and $Q'$.
+It means that there exists an FH-bisimulation $\mathcal{R}_{Q,Q'}$ relating the two pNets $Q$ and $Q'$.
 We define a relation $\mathcal{R}$ relating states of $P[Q]_{j_0}$ with states of $P[Q']_{j_0}$:
@@
 
-By the decomposition lemma for OTs (Lemma~\ref{lem-decompose}), we obtain the 2 following OTs (equality side-conditions have been inlined for clarity):
+By the decomposition lemma for OTs (Lemma~\ref{lem-decompose}), we obtain the 2 following OTs (equality side-conditions have been unlined for clarity):
 \begin{mathpar}
@@
 By definition of $\mathcal{R}$ we have 
-$(S_Q,S_{Q'}| \Pred_{Q,Q'})\in\mathcal{R}_{Q,Q'}$. And thus, by definition of weak FH-bisimulation, there exist a family of weak open transitions $WOT_{x}$:
+$(S_Q,S_{Q'}| \Pred_{Q,Q'})\in\mathcal{R}_{Q,Q'}$. And thus, by definition of weak FH-bisimulation, there exists a family of weak open transitions $WOT_{x}$:
  \begin{mathpar}
@@
  \begin{proof}   Consider $P$ weak FH-bisimilar to $P'$.
-There exists a FH-bisimulation $\mathcal{R}_{P,P'}$ relating $P$ and $P'$.
+There exists an FH-bisimulation $\mathcal{R}_{P,P'}$ relating $P$ and $P'$.
 We define a relation $\mathcal{R}$ relating states of $P[Q]_{j_0}$ with states of $P'[Q]_{j_0}$:
@@
 By definition of $\mathcal{R}$ we have 
-$(S_P,S_{P'}, \Pred_{P,P'})\in\mathcal{R}_{P,P'}$. And thus, by definition of weak FH-bisimulation, there exist a family of weak open transitions $WOT_{x}$:
+$(S_P,S_{P'}, \Pred_{P,P'})\in\mathcal{R}_{P,P'}$. And thus, by definition of weak FH-bisimulation, there exists a family of weak open transitions $WOT_{x}$:
  \begin{mathpar}
@@
 We here need a special case of Lemma~\ref{lem-Weakcompose} where the inner pNet $Q$ does a simple OT.
-This is just a particular case of the theorem but where notations get simplified because the inner pnet does a single transition.
+This is just a particular case of the theorem but where notations get simplified because the inner pNet does a single transition.
  This way we can compose the WOTs of $P'$ with the OT of $Q$ and obtain, with $\gamma_{j_0}=[\beta] $:
@@
 \medskip
-Then for all $\tau$ transitions above we have a similar WOT that include a non-$\tau$ move from an external action of P or Q, like for example:
+Then for all $\tau$ transitions above we have a similar WOT that include a non-$\tau$ move from an external action of $P$ or $Q$, like for example:
 

### 2021-10-21 2016-Weak-FH-Bisim/WeakBisim.tex
annex review

@@
           {t \OTarrow {\alpha} t'}\in\mathcal{T}
-\implies
+\quad\implies\quad
     \openrule
@@
      \land \alpha\!=\!\alpha_x \land  
-     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}
+     \Pred_{s',t_x}\subst{\Post_{OT}\!\uplus\!\Post_{OT_x}}\right)}
 \end{multline*}
@@
 		}%\]
-	\vspace{-2.2ex}\\\text{and~~}
+	\vspace{-2.2ex}\\\text{and~\qquad\qquad~}
 		%\[
@@
 \begin{lemma}[Open transition composition]\label{lem-compose} 
-	Suppose $j_0\in J$ and:\\[-2ex]
+	Suppose $j_0\in J$ and:\\[-1ex]
 \begin{mathpar}
@@
 }%\]
-\text{~~and~~}
+\quad\text{~~and~~}\quad
 %\[
@@
 \end{mathpar}
-Then, we have:\\[-2ex]
+Then, we have:\\[-1ex]
 	\[ P[Q]_{j_0}  
@@
  \implies \bigvee_{x\in X}
-       	\left( \forall j. \beta_j=\beta_{jpx}  \land \Pred_{OT_{px}}
+       	\Big( \forall j. \beta_j=\beta_{jpx}  \land \Pred_{OT_{px}}
        	\land \alpha\!=\!\alpha_{px} \land
-       	\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\right)
+       	\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\Big)
 \end{multline*}
@@
        	\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}\!
-       	\left( \forall j.\beta_{jpx}\!=\!\beta_{jpxy} \land\! \Pred_{OT_{pxy}}\!
+       	\Big( \forall j.\beta_{jpx}\!=\!\beta_{jpxy} \land\! \Pred_{OT_{pxy}}\!
        	\land\! \alpha_{px}\!=\!\alpha_{pxy} \!\land\!
-       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}\!\uplus\!\Post_{OT_{pxy}}}\right)}
+       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}\!\uplus\!\Post_{OT_{pxy}}}\Big)}
 \end{multline*}
@@
        		\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
-       		\left( \forall j. \beta_j=\beta_{jpxy}  \land \Pred_{OT_{pxy}}
+       		\Big( \forall j. \beta_j=\beta_{jpxy}  \land \Pred_{OT_{pxy}}
        		\land \alpha\!=\!\alpha_{pxy} \land
-       		\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{pxy}}}\right)}$.
+       		\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{pxy}}}\Big)}$.
        	\end{small}
@@
        		\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}
-       		\left( \forall j. \beta_j=\beta_{jpx}  \land \Pred_{OT_{px}}
+       		\Big( \forall j. \beta_j=\beta_{jpx}  \land \Pred_{OT_{px}}
        		\land \alpha\!=\!\alpha_{px} \land
-       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\right)\land\Pred_{p,u}}\\
+       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\Big)\land\Pred_{p,u}}\\
        		%
        		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-       		\left( \forall j. \beta_j=\beta_{jpx}  \land 
+       		\Big( \forall j. \beta_j=\beta_{jpx}  \land 
        		(\Pred_{OT_{px}}\land\Pred_{p,u})
        		\land \alpha\!=\!\alpha_{px} \land
-       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\right)\\
+       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\Big)\\
        		%
        		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
-       		\big( \forall j. \beta_j=\beta_{jpx}  \land (\bigvee_{y\in Y} 
-       		\big( \forall j'. \beta_{j'px}=\beta_{j'pxy}  \land \Pred_{OT_{pxy}}
+       		\Big( \forall j. \beta_j=\beta_{jpx}  \land \bigvee_{y\in Y} 
+       		\Big( \forall j'. \beta_{j'px}=\beta_{j'pxy}  \land \Pred_{OT_{pxy}}
        		\land \alpha_{px}\!=\!\alpha_{pxy}\\~\hspace*{2em}~ \land
-       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}\big))
+       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}\uplus\Post_{OT_{pxy}}}\Big)
        		\land \alpha\!=\!\alpha_{px} \land
-       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\big)\\
+       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\Big)\\
        		%
        		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X} \bigvee_{y\in Y}
-       		\big( \forall j, j'. \beta_j=\beta_{jpx} \land \beta_{j'px}=\beta_{j'pxy}
-       		\land \big( 
+       		\Big( \forall j, j'. \beta_j=\beta_{jpx} \land \beta_{j'px}=\beta_{j'pxy}
+       		\land \Big( 
        		\Pred_{OT_{pxy}}
@@
        		\land
-       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\big)\big)
+       		\Pred_{{px}}\subst{\Post_{OT}\uplus\Post_{OT_{px}}}\Big)\Big)
        		$
@@
  \bigvee_{x\in X} \bigvee_{y\in Y}
-\big( \forall j, j'.\beta_j=\beta_{jpx} \land \beta_{j'px}=\beta_{j'pxy}
+\Big( \forall j, j'.\beta_j=\beta_{jpx} \land \beta_{j'px}=\beta_{j'pxy}
 \land \Pred_{OT_{pxy}}\\
-~\hspace*{3em}~\land \alpha\!=\!\alpha_{px}\!=\!\alpha_{pxy}\land\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus \Post_{OT_{pxy}}}\big)
+~\hspace*{8.5em}~\land \alpha\!=\!\alpha_{px}\!=\!\alpha_{pxy}\land\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus \Post_{OT_{pxy}}}\Big)
 \\
 {~}\hspace{1cm}~ \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
-\left( \forall j. \beta_j\!=\!\beta_{jpxy}  \land \Pred_{OT_{pxy}}
+\Big( \forall j. \beta_j\!=\!\beta_{jpxy}  \land \Pred_{OT_{pxy}}
 \land \alpha\!=\!\alpha_{pxy} \land
-\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{pxy}}}\right)$
+\Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{pxy}}}\Big)$
   \end{small}
@@
  \implies$\\ $\displaystyle{\bigvee_{x\in X}
- \left( \forall j\in J\cap \Holes(Q). \beta_j\!=\!\beta_{jx}\!  \land\! 
+ \Big( \forall j\in J\cap \Holes(Q). \beta_j\!=\!\beta_{jx}\!  \land\! 
  \Pred_{OT_x}
  \land \alpha_Q\!=\!\alpha_x \land  
- \Pred_{s, x}\subst{\Post\,''\uplus\Post_{OT_x}}\right)}$
+ \Pred_{s, x}\subst{\Post\,''\uplus\Post_{OT_x}}\Big)}$
 
@@
  	{\displaystyle\bigvee_{x\in X}
- 	\left( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \land 
+ 	\Big( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \land 
  	\Pred_{OT_x}
  	\land \alpha_Q\!=\!\alpha_x \land  
- 	\Pred_{s,x}\subst{\Post\,''\uplus\Post_{OT_x}}\right)\land
- }
- \\ \Pred\,'\land\alpha_Q=\beta_{j_0} \\
+ 	\Pred_{s,x}\subst{\Post\,''\uplus\Post_{OT_x}}\Big)\land
+ }
+ \\~~\hspace*{3.5em}~\Pred\,'\land\alpha_Q=\beta_{j_0} \\
  	\implies
@@
  	{\displaystyle\bigvee_{x\in X}
- 		( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \land 
+ 		\Big( \forall j\in J\cap \Holes(Q). \beta_j=\beta_{jx}  \land 
  		\Pred\,'\land \Pred_{OT_x}
  		\land \alpha_Q\!=\!\alpha_x \land \alpha_Q\!=\!\beta_{j_0 x}\, \land} \\ 
- 		\Pred_{s, x}\subst{\Post\,''\uplus\Post_{OT_x}})
+ 		~\hspace*{3.5em}~ \Pred_{s, x}\subst{\Post\,''\uplus\Post_{OT_x}}\Big)
  	 $\end{small}
@@
 {\displaystyle\bigvee_{x\in X}
- 		\!\left( \forall j\in J. \beta_j=\beta_{jx} \! \land\! 
- 		\big(\Pred\,'\land\! \Pred_{OT_x}
- 		 \land \alpha_Q\!=\!\beta_{j_0 x}\right)\! \land\! \alpha_Q\!=\!\alpha_x\land\!  \Pred_{s, x}\subst{\Post\,''\!\uplus\!\Post_{OT_x}}\big)
+ 		\!\Big( \forall j\in J. \beta_j=\beta_{jx} \! \land\! 
+ 		\left(\Pred\,'\land\! \Pred_{OT_x}
+ 		 \land \alpha_Q\!=\!\beta_{j_0 x}\right)\! \land\! \alpha_Q\!=\!\alpha_x\land\!  \Pred_{s, x}\subst{\Post\,''\!\uplus\!\Post_{OT_x}}\Big)
  		}$
@@
 		 \!\!\implies\!\!\! \bigvee_{x\in X}\!
-			\left( \forall j\in J'. \beta_j=\beta_{jx}\!  \land\! 
+			\Big( \forall j\in J'. \beta_j=\beta_{jx}\!  \land\! 
 			\Pred_{OT_x}\!
 			\land\! \alpha\!=\!\alpha_x\! \land\!  
-			\Pred_{s,x}\subst{\Post\,'\uplus\Post_{OT_x}}\right)}$
+			\Pred_{s,x}\subst{\Post\,'\uplus\Post_{OT_x}}\Big)}$
 			%     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x}) \right)$.
@@
 {~}\hspace{1cm}~ \implies  \hspace{-2ex}
-{\displaystyle{\bigvee_{x\in X}\!(\forall j\!\in\! J'. \beta_j\!=\!\beta_{jx}  
+{\displaystyle{\bigvee_{x\in X}\!\Big(\forall j\!\in\! J'. \beta_j\!=\!\beta_{jx}  
 \!\land \!
@@
 \land \Pred_{s, x}\subst{\Post\,'\uplus\Post_{OT_x}}) \land
-\Pred\,''\\ % 
+\Pred\,''\Big)\\ % 
 			%FH for P
@@
 by hypothesis we have $(s,t|\Pred_{s,t})\in\mathcal{R}$  and $s=s_{10}$.
-Thus, by  Definition \ref{def-Weak-bisim} we  can deduce there exist weak open transitions $\symb{WOT}_a^{a\in A} \subseteq \WT_2$:
+Thus, by  Definition \ref{def-Weak-bisim} we  can deduce there exists an indexed set of weak open transitions $\symb{WOT}_a^{a\in A} \subseteq \WT_2$:
  \begin{mathpar}
@@
 we have  $(s_{11},u_a|\Pred_{s_{11},a})\in \mathcal{R}$  and $s_{11}=s_{20}$. Again 
- by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{b}^{b\in B} \subseteq \WT_2$:
+ by Definition \ref{def-Weak-bisim} we can deduce there exists an indexed set of weak open transitions $\symb{WOT}_{b}^{b\in B} \subseteq \WT_2$:
  \begin{mathpar}
@@
 From previous case, we have $(s_{21},v_{b}|\Pred_{s_{21},b})\in \mathcal{R}$, and we have $s_{21}=s_{30}$. Then, by
- Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{a}^{c\in C} \subseteq \WT_2$:
+ Definition \ref{def-Weak-bisim} there exists an indexed set of weak open transitions $\symb{WOT}_{a}^{c\in C} \subseteq \WT_2$:
  \begin{mathpar}
@@
  \displaystyle{\bigvee_{x\in X}} 
-  ( \forall j\in J. \gamma_j'=\gamma_{j}  \land \Pred
+  \left( \forall j\in J. \gamma_j'=\gamma_{j}  \land \Pred
      \land \alpha \!=\! \alpha'' \land  
-     \Pred_{s',x}\subst{\Post_{OT}\uplus\Post\,})$\\
+     \Pred_{s',x}\subst{\Post_{OT}\uplus\Post\,}\right)$\\
 We have:\\
@@
 \begin{multline*}
-(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies \\
+\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies \\
  \bigvee_{a\in A}
-  \!\! ( \forall j\in J_a. \vis{\beta_{1j}}\!=\!\gamma_{ja}\!  \land\! \Pred_{OT_a}\! \land\!
-     \Pred_{s_{11},a}\subst{\Post_1\uplus\Post_{OT_a}}) \wedge \Pred_2\subst{\Post_1\uplus\Post_{OT_a}}  \hspace{-2ex}
+  \!\! \left( \forall j\in J_a. \vis{\beta_{1j}}\!=\!\gamma_{ja}\!  \land\! \Pred_{OT_a}\! \land\!
+     \Pred_{s_{11},a}\subst{\Post_1\uplus\Post_{OT_a}} \wedge \Pred_2\subst{\Post_1\uplus\Post_{OT_a}} \right) \hspace{-2ex}
 \end{multline*}
@@
 \begin{multline*}
-(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies\\
+\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies\\
 \bigvee_{a\in A}
@@
 By replacing the inner predicate $(\Pred_{s_{11},u_a}\wedge\Pred_2)$ by the conclusion of the  statement given in case 2,  the formula becomes: 
-\begin{multline*}(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies\\
+\begin{multline*}\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies\\
 {\bigvee_{a\in A}}
-   \!\!(\forall j\in J_a. \vis{\beta_{1j}}\!\!=\!\gamma_{ja}  \land \Pred_{OT_a}
-      \land ({\bigvee_{b\in B}}(
+   \!\!\Big(\forall j\in J_a. \vis{\beta_{1j}}\!\!=\!\gamma_{ja}  \land \Pred_{OT_a}
+      \land \Big({\bigvee_{b\in B}}(
     \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}  \land \Pred_{OT_{b}}\!\land 
-    \alpha'\!=\!\alpha_{2 b} \land\\ \Pred_{s_{21},b}\subst{\Post_2\uplus\Post_{OT_{b}}})\subst{\Post_1\uplus\Post_{OT_a}})
+    \alpha'\!=\!\alpha_{2 b} \land\\ \Pred_{s_{21},b}\subst{\Post_2\uplus\Post_{OT_{b}}})\subst{\Post_1\uplus\Post_{OT_a}}\Big)\Big)
 \end{multline*}
@@
 This can be rewritten into:
-\begin{multline*}(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1} \implies\\
+\begin{multline*}\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1} \implies\\
 {\bigvee_{a\in A}}\, {\bigvee_{b\in B}} 
-(\forall j\in J_a.
+\Big(\forall j\in J_a.
 \vis{\beta_{1j}}\!\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-\vis{\beta_{2j}}\!=\!\gamma_{jb}\subst{\Post_1\uplus\Post_{OT_a}}   \land\Pred_{OT_a} \land \\ \Pred_{OT_{b}} \subst{\Post_1\uplus\Post_{OT_a}} \land  (\alpha'\!=\!\alpha_{2 b}) \subst{\Post_1\uplus\Post_{OT_a}} \land \\ \Pred_{s_{21},b}\subst{\Post_2\shortodot\Post_1\uplus \Post_{OT_{b}}\shortodot \Post_{OT_a}})
+\vis{\beta_{2j}}\!=\!\gamma_{jb}\subst{\Post_1\uplus\Post_{OT_a}}   \land\Pred_{OT_a} \land \\ \Pred_{OT_{b}} \subst{\Post_1\uplus\Post_{OT_a}} \land  (\alpha'\!=\!\alpha_{2 b}) \subst{\Post_1\uplus\Post_{OT_a}} \land \\ \Pred_{s_{21},b}\subst{\Post_2\shortodot\Post_1\uplus \Post_{OT_{b}}\shortodot \Post_{OT_a}}\Big)
 \end{multline*}
@@
 As well $\Post_{OT_a}$  does not act on $\alpha'$, nor on  $\beta_{2j}$ the formula can be simplified as follows:
-\begin{multline*}(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies\\
+\begin{multline*}\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1}\implies\\
 \displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}} 
-(\forall j\in J_a.
+\Big(\forall j\in J_a.
 \vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-\vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jb} \subst{\Post_{OT_a}}  \land\Pred_{OT_a} \land \\ \Pred_{OT_{b}} \subst{\Post_{OT_a}} \land \alpha'\subst{\Post_1}=\alpha_{2 b} \subst{\Post_{OT_a}} \land\\ \Pred_{s_{21},b}\subst{\Post_2\shortodot\Post_1\uplus \Post_{OT_{b}}\shortodot \Post_{OT_a}})\end{multline*}
+\vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jb} \subst{\Post_{OT_a}}  \land\Pred_{OT_a} \land \\ \Pred_{OT_{b}} \subst{\Post_{OT_a}} \land \alpha'\subst{\Post_1}=\alpha_{2 b} \subst{\Post_{OT_a}} \land\\ \Pred_{s_{21},b}\subst{\Post_2\shortodot\Post_1\uplus \Post_{OT_{b}}\shortodot \Post_{OT_a}}\Big)\end{multline*}
 Finally, the conjunction with the term $\Pred_3\subst{\Post_2\shortodot\Post_1}$ of the both sides of the implication and rewriting, we get:
-\begin{multline*}(\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortodot\Post_1}\implies \\
+\begin{multline*}\Pred_{s,t} \land \Pred_1)\wedge\Pred_2\subst{\Post_1} \land \Pred_3\subst{\Post_2\shortodot\Post_1}\implies \\
 \displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}} 
-(\forall j\in J_a.\vis{\beta^1_j}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
-\vis{\beta_{2j}}\subst{\Post_1}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}\land \Pred_{OT_a}\land\\\Pred_{OT_{b}}\subst{\Post_{OT_a}} \land  \alpha'\subst{\Post_1}= \alpha_{2 b} \subst{\Post_{OT_a}} \land (\Pred_{s_{21},v_b} \land  \Pred_3)\\ \subst{\Post_2\shortodot \Post_1\uplus \Post_{OT_{b}}\shortodot\Post_{OT_a}})\end{multline*}
+\Big(\forall j\in J_a.\vis{\beta^1_j}\!=\!\gamma_{ja} \land  \forall j \in J_{b}.
+\vis{\beta_{2j}}\subst{\Post_1}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}\land \Pred_{OT_a}\land\\\Pred_{OT_{b}}\subst{\Post_{OT_a}} \land  \alpha'\subst{\Post_1}= \alpha_{2 b} \subst{\Post_{OT_a}} \land (\Pred_{s_{21},v_b} \land  \Pred_3)\\ \subst{\Post_2\shortodot \Post_1\uplus \Post_{OT_{b}}\shortodot\Post_{OT_a}}\Big)\end{multline*}
 Again note that because of the domain  of the substitution function is independent from some predicates and expressions, we removed $\Post_1$ and  we  added the term $\Post_{OT_{b}}\shortodot\,\Post_{OT_a}$ in the substitution of the right side of the implication.\\
@@
  {\bigvee_{a\in A}}\, {\bigvee_{b\in B}}\, {\bigvee_{c\in C}} 
-(\forall\! j\in\! J_a.\vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \!\in\! J_{b}.\vis{\beta_{2j}\subst{\Post_{OT_a}}}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}  \land \\
+\Big(\forall\! j\in\! J_a.\vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \!\in\! J_{b}.\vis{\beta_{2j}\subst{\Post_{OT_a}}}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}  \land \\
  \forall j\!\in\! J_{c}. \vis{\beta_{3j} \subst{\Post_2\,\shortodot\,\Post_1}} \!=\!\gamma_{jc} \subst{\Post_{OT_{b}}\shortodot\Post_{OT_a}}  \land\\
    \underbrace{\Pred_{OT_a}\land\Pred_{OT_{b}} \subst{\Post_{OT_a}} \land 
-  \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortodot\Post_{OT_a}}}_{\Pred} \land  \underbrace{\alpha'\subst{\Post_1}}_{\alpha}=\underbrace{\alpha_{2 b} \subst{\Post_{OT_a}}}_{\alpha''} \\\land \Pred_{s_{31},c}  \subst{\underbrace{\Post_3\shortodot\Post_2\shortodot\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{c}}\shortodot \Post_{OT_{b}}\shortodot\Post_{OT_a}}_{\Post}})
+  \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortodot\Post_{OT_a}}}_{\Pred} \land  \underbrace{\alpha'\subst{\Post_1}}_{\alpha}=\underbrace{\alpha_{2 b} \subst{\Post_{OT_a}}}_{\alpha''} \\\land \Pred_{s_{31},c}  \subst{\underbrace{\Post_3\shortodot\Post_2\shortodot\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{c}}\shortodot \Post_{OT_{b}}\shortodot\Post_{OT_a}}_{\Post}}\Big)
 \end{multline*}
@@
 \displaystyle{\bigvee_{a\in A}}\, \displaystyle{\bigvee_{b\in B}}\, \displaystyle{\bigvee_{c\in C}} 
-(\forall j\in J.\gamma_j'=\gamma_j \land  \Pred \land \alpha=\alpha''  \land \Pred_{s',c}\subst{\Post_{OT}\uplus\Post\,}$\\
+\Big(\forall j\in J.\gamma_j'=\gamma_j \land  \Pred \land \alpha=\alpha''  \land \Pred_{s',c}\subst{\Post_{OT}\uplus\Post\,}\Big)$\\
 
@@
  \displaystyle{\bigvee_{x\in X}} 
-(\forall j\in J.\gamma_j'=\gamma_j \land  \Pred \land \alpha=\alpha''  \land \Pred_{s',x}\subst{\Post_{OT}\uplus\Post\,}$\\
+\Big(\forall j\in J.\gamma_j'=\gamma_j \land  \Pred \land \alpha=\alpha''  \land \Pred_{s',x}\subst{\Post_{OT}\uplus\Post\,}\Big)$\\
 \end{proof}
@@
 
-Note that for all $j\in J\setminus \Holes(Q)$, $\gamma_j' = \gamma_j$ because for all $l$ $\Post\,'_{1l}$ coincide with $\Post_{1l}$ on the variables of $\beta_{1ij}$, and similarly for $\Post\,'_2$ and $\Post\,'_{3l}$.
+Note that for all $j\in J\setminus \Holes(Q)$, $\gamma_j' = \gamma_j$ because for all $l$ $\Post\,'_{1l}$ coincides with $\Post_{1l}$ on the variables of $\beta_{1ij}$, and similarly for $\Post\,'_2$ and $\Post\,'_{3l}$.
 %Concerning $\gamma'_{j_0}$ we have:
@@
 		\land \!\!\bigwedge_{p=0}^n\Big((\alpha_p\subst{\bigodot_{i=p-1}^{0}\Post_i}) = \beta_p\land (\Pred_p\subst{\bigodot_{i=p-1}^{0}\Post_i}) \Big)}\]
-Indeed,
+Indeed we have:
 \begin{scriptsize}
@@
 	\]
-Where
+where
 {\small 
@@
 \Pred_{Q,Q'}\land \Pred_Q \implies \\
-\bigvee_{x\in X}
+\Big(\bigvee_{x\in X}
 (\forall j\in J_Q.\, \vis{\beta_j}=\gamma_{j x})\Rightarrow (\Pred_{Q_x}\land%\\ %&~~
-\alpha_Q=\alpha_x \land \Pred_{Q,Q' x}\subst{\Post_{Q' x}\uplus \Post_{Q}}) 
+\alpha_Q=\alpha_x \land \Pred_{Q,Q' x}\subst{\Post_{Q' x}\uplus \Post_{Q}}) \Big)
 \end{multline*}
@@
 \Big(\bigvee_{x\in X}
-(\forall j\in J_P.\, \vis{\beta_j}=\gamma_{j x} \land \vis{\alpha_Q}=\gamma_{j_0})\Rightarrow (\Pred_{P'_x}\land\\ &~~\alpha=\alpha_x \land \Pred_{P,P' x}\subst{\Post_{P' x}\uplus \Post_{P}}) \Big)
+(\forall j\in J_P.\, \vis{\beta_j}=\gamma_{j x} \land \vis{\alpha_Q}=\gamma_{j_0})\Rightarrow\\ & \quad (\Pred_{P'_x}\land \alpha=\alpha_x \land \Pred_{P,P' x}\subst{\Post_{P' x}\uplus \Post_{P}}) \Big)
 \end{split}
@@
 
-         Note: if we were using the alternative weak bisimulation relation from Appendix \ref{app-WFH-equiv}, Lemma \ref{lem-rel-OT-WOT}, that is checking strong bisimulation between the corresponding
+         Note that if we were using the alternative weak bisimulation relation from Appendix \ref{app-WFH-equiv}, Lemma \ref{lem-rel-OT-WOT}, that is checking strong bisimulation between the corresponding
 weak automaton, we would have a more transitions coverage to examine, as we have 4 weak transitions for $b0$ in the \symb{SimpleProtocolSpec} weak automaton, and 7 WOTs (including 4 

### 2021-10-21 2016-Weak-FH-Bisim/WeakBisim.tex
Minor

@@
 \noindent
-\begin{minipage}{0.67\linewidth} 	Suppose 
+	Suppose 
    $A_1 = \mylangle J,\mathcal{S}_1, s_0,V_1,
@@
 the following:
+
+ \begin{itemize}
+ \item   
+For any open transition $OT$ in $\mathcal{T}_1$:\\
+\begin{minipage}{0.67\linewidth}  \begin{mathpar}
+     \openrule
+         {
+           \beta_j^{j\in J'},\Pred_{OT},\Post_{OT}}
+         {s \OTarrow {\alpha} s'}
+
+\end{mathpar}
+ there exists an indexed set of  open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
+ \begin{mathpar}
+%    \left( fresh \ \set{\alpha_i}, \set{b_j}, v_x.\ \
+    \openrule
+         {
+           \beta_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
+         {t \OTarrow {\alpha_x} t_x}
+%         \right)
+\end{mathpar}
+
 \end{minipage}
@@
 \begin{minipage}{0.30\linewidth}
-	\includegraphics[width=\linewidth]{XFIG/Bisim}
+\vspace{-2em}
+{	\includegraphics[width=\linewidth]{XFIG/Bisim}}
 \end{minipage}
-
- \begin{itemize}
- \item  For any open transition $OT$ in $\mathcal{T}_1$:
- \begin{mathpar}
-     \openrule
-         {
-           \beta_j^{j\in J'},\Pred_{OT},\Post_{OT}}
-         {s \OTarrow {\alpha} s'}
-
-\end{mathpar}
- there exists an indexed set of  open transitions $OT_x^{x\in X} \subseteq \mathcal{T}_2$:
- \begin{mathpar}
-%    \left( fresh \ \set{\alpha_i}, \set{b_j}, v_x.\ \
-    \openrule
-         {
-           \beta_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
-         {t \OTarrow {\alpha_x} t_x}
-%         \right)
-\end{mathpar}
  such that  $\forall x.\, J'=J_{x}$ and there exists $\Pred_{s',t_x}$ such that $(s',t_x|\Pred_{s',t_x})\in 
@@
 define a
-predicate $\Predsv$ relating a synchronisation vector (of the form $\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
-{\alpha'} 
-{e_b}$),
+predicate $\Predsv$ relating a synchronisation vector (of the form $\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}}{\alpha'} {e_b}$),
 the actions of the involved sub-pNets and the resulting actions.
@@
 \begin{multline*}
-\Predsv \Big(\left(\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}} 
-{\alpha'} 
-{e_b}\right), \alpha_i^{i\in I}, \beta_j^{j\in J}, \alpha\Big)\Leftrightarrow \\~\qquad\qquad%\bigg(
-%
-%\exists {(\alpha'_i)}^{i\in I},
-%{(\beta'_j)}^{j\in J},v'.\, SV=
-%\\~~\land
+\Predsv \Big(
+\big({\SV{{(\alpha'_i)}^{i\in I}, {(\beta'_j)}^{j\in J}}{\alpha'}{e_b}}\big)
+, \alpha_i^{i\in I}, \beta_j^{j\in J}, \alpha\Big)\Leftrightarrow \\
 \forall i\in I.\, \alpha_i=\alpha'_i\land \forall j \in J.\, \beta_j=\beta'_j \land 

### 2021-10-22 2016-Weak-FH-Bisim/2021-09-letter2Reviewers.tex
small pass letter

@@
 \begin{quote}
-$\otimes$ is a form of composition: we have changed for something similar to the functional composition symbol $\circ$, renamed it into $\odot$
+$\otimes$ is a form of composition: we have changed for something similar to the functional composition symbol $\circ$, we chose the $\odot$ symbol and hope it is less confusing
 \end{quote}

### 2021-10-22 2016-Weak-FH-Bisim/WeakBisim.tex
typos and lmcs style

@@
 equivalence on open automata and derives weak bisimilarity for pNets,
-together with properties on compositionality of weak bisimulaiton for
+together with properties on compositionality of weak bisimulation for
 open pNets. 
@@
 Consider a pNet node that assembles several pLTSs, the synchronisation vectors specify the way that transitions of the composed pNet are built from the transitions of the sub-nets.
-This can be seen as "conditional transtions" of the pNet, or alternatively, as a syntax to encode structural operational semantics (SOS rules) of the system: each vector expresses not only the actions emitted by the pNet but also what transitions of the composed pLTSs must occur to trigger this global transition.
+This can be seen as "conditional transitions" of the pNet, or alternatively, as a syntax to encode structural operational semantics (SOS rules) of the system: each vector expresses not only the actions emitted by the pNet but also what transitions of the composed pLTSs must occur to trigger this global transition.
 Synchronisation vectors can also express the exportation of an action of a sub-pNet to the next level, or to hide an interaction and make it non-observable.
@@
 The full system implementation should be equivalent (e.g.  weakly bisimilar)
-to thhis $\symb{SimpleProtocolSpec}$.  
+to this $\symb{SimpleProtocolSpec}$.  
 The pNet has a tree-like structure.
@@
 
-\begin{theorem}[FH-Bisimulation is an equivalence]\label{thm-equiv} Suppose $\mathcal{R}$ 
-is an FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
+\begin{thm}[FH-Bisimulation is an equivalence]\label{thm-equiv} Suppose $\mathcal{R}$ 
+is an FH-bisimulation. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
 reflexive, symmetric and transitive.
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{theorem}[Decidability of FH-bisimulation]
+\begin{thm}[Decidability of FH-bisimulation]
 Let $A_1$ and $A_2$ be finite open automata
@@
 
-\end{theorem}
+\end{thm}
 
@@
 predicates.
-\begin{lemma}[Open transition decomposition\label{lem-decompose}] Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$}.
+\begin{lem}[Open transition decomposition\label{lem-decompose}] Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$}.
 	Let $\Leaves(Q)=p_l^{l\in L_Q}$ and suppose:
@@
 		$Q$.
-\end{lemma}
+\end{lem}
 
@@
 
-\begin{lemma}[Open transition composition]\label{lem-compose} 
+\begin{lem}[Open transition composition]\label{lem-compose} 
 	Suppose $j_0\in J$ and:\\[-1ex]
@@
 	\]
-\end{lemma}
+\end{lem}
 
@@
 
-\begin{theorem}[Congruence]\label{thm-congr-eq}
+\begin{thm}[Congruence]\label{thm-congr-eq}
 	Consider an open pNet:
@@
 	$\pNet[\pNetQ']_{j_0}$ are FH-bisimilar.
-\end{theorem}
-
-\begin{theorem}[Context equivalence]\label{thm-ctxt-eq}
+\end{thm}
+
+\begin{thm}[Context equivalence]\label{thm-ctxt-eq}
 	Consider two  open pNets
@@
 	$\pNet'[Q]_{j_0}$ are FH-bisimilar.
-\end{theorem}
+\end{thm}
 
@@
 composability and FH-bisimilarity.
-\begin{theorem}[Composability] \label{thm-composability}
+\begin{thm}[Composability] \label{thm-composability}
 	Consider two FH-bisimilar pNets with an arbitrary number of holes, when replacing, 
@@
 	obtain two FH-bisimilar pNets.
-\end{theorem}
+\end{thm}
 This theorem is quite powerful.
@@
 
-\begin{theorem}[Weak FH-Bisimulation is an equivalence]\label{thm-weak-equiv} Suppose $\mathcal{R}$ 
+\begin{thm}[Weak FH-Bisimulation is an equivalence]\label{thm-weak-equiv} Suppose $\mathcal{R}$ 
 is a weak FH-bisimulation. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
 reflexive, symmetric and transitive.
-\end{theorem}
+\end{thm}
 The proof  is detailed in Appendix \ref{app-WFH-equiv}, it follows a similar pattern as the proof that strong FH-bisimulation is an equivalence, but technical details are different, and in practice we rely on a variant of the definition of weak FH-bisimilarity; this equivalent version simulates a \emph{weak} open transition with a set of weak open transition.
@@
 
-\begin{theorem}[Congruence for  weak bisimulation]\label{weak-thm-congr-eq}
+\begin{thm}[Congruence for  weak bisimulation]\label{weak-thm-congr-eq}
 	Consider an open pNet $P$
@@
 	$\pNet[\pNetQ']_{j_0}$ are weak FH-bisimilar.
-\end{theorem}
-
-\begin{theorem}[Context equivalence for  weak bisimulation]\label{weak-thm-ctxt-eq}
+\end{thm}
+
+\begin{thm}[Context equivalence for  weak bisimulation]\label{weak-thm-ctxt-eq}
 	Consider two  open pNets
@@
 	$\pNet'[\pNetQ]_{j_0}$ are weak FH-bisimilar.
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{theorem}[Composability of weak bisimulation]\label{weak-compos}
+\begin{thm}[Composability of weak bisimulation]\label{weak-compos}
 	Consider two weak FH-bisimilar pNets with an arbitrary number of holes, such that the two pNets cannot observe silent actions. When replacing, 
@@
 	obtain two weak FH-bisimilar pNets.
-\end{theorem}
+\end{thm}
 
@@
 In this last area, we can mention
-Calder's work \cite{calder2001symbolic}, that  defines a symbolic semantic for full LOTOS, with a symbolic bisimulation over it;
+Calder's work \cite{calder2001symbolic}, that  defines a symbolic semantic for full Lotos, with a symbolic bisimulation over it;
 Borgstrom et al., Liu et al, Delaune et al.
@@
  Feng et al. provide a symbolic bisimulation for quantum processes \cite{feng2014symbolic}.
-All the above works, didn't give a complete approach for verification, and the models on which these works based are definitely different from ours.
+All the above works, did not give a complete approach for verification, and the models on which these works based are definitely different from ours.
 
@@
 
-\bibliographystyle{lncs/splncs}
+\bibliographystyle{alpha}
 
@@
 %       
-              \begin{proof}
-
+%              \begin{proof}
+       	\proof
        	It is trivial to check reflexivity and symmetry. Here we focus on the
@@
 
-       \end{proof}
+%       \end{proof}
+\qed
 
@@
 
-   \begin{proof}
-
+%   \begin{proof}
+\proof
 Consider rule \TrDeux\ in 
@@
  \end{small}
-\end{proof}
+%\end{proof}
+  \qedhere
 
@@
 
-\begin{proof} 
+\proof
+%\begin{proof} 
 Let $P=\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle$.
@@
 \end{small}
-   This provides the desired conclusion.     \end{proof}
+   This provides the desired conclusion.   
+%  \end{proof}
+\qed
 
@@
 
-\begin{lemma}[Open transition composition -- inactive]\label{lem-compose-2} ~\\	This lemma is the simple case where the pNet filling the hole is not involved in the transition.
+\begin{lem}[Open transition composition -- inactive]\label{lem-compose-2} ~\\	This lemma is the simple case where the pNet filling the hole is not involved in the transition.
 Suppose $j_0\not\in J$ and $L_Q=\Leaves({Q})$:\\[-2ex]
@@
 	\]
-\end{lemma}
+\end{lem}
 The proof is trivial.
@@
 \medskip
-\begin{proof}
+%\begin{proof}
+\proof
  The proof of Theorem~\ref{thm-congr-eq} exhibits classically a bisimulation relation for 
@@
  similar.
-\end{proof}
-
+%\end{proof}
+\qed
         \subsection{Proof of Theorem ~\ref{thm-ctxt-eq}: Context equivalence}
@@
 \medskip
-
-\begin{proof}
+\proof
+%\begin{proof}
 The proof of Theorem~\ref{thm-ctxt-eq} exhibits  a bisimulation relation for a 
@@
 similar.
-\end{proof}
+%\end{proof}
+\qed
 
@@
 
-\begin{lemma}[Alternative definition of weak open transitions]
+\begin{lem}[Alternative definition of weak open transitions]
 \label{lem-rel-OT-WOT} Let $A = \mylangle J,\mathcal{S}, s_0,V_1,
@@
 \end{enumerate}
-\end{lemma}
-
-\begin{proof} ($\Rightarrow$) We present an induction on $n$ and $m$, focusing on the incrementation on $n$: we prove that the property is valid for $m=-1$, $n=-1$ apply a first induction proof for going from $n$ to $n+1$, a similar induction can be applied to go from $m$ to $m+1$ (omitted).
+\end{lem}
+\proof %\begin{proof}
+ ($\Rightarrow$) We present an induction on $n$ and $m$, focusing on the incrementation on $n$: we prove that the property is valid for $m=-1$, $n=-1$ apply a first induction proof for going from $n$ to $n+1$, a similar induction can be applied to go from $m$ to $m+1$ (omitted).
 \begin{itemize}
@@
 \end{itemize}
-\end{proof}
-
-\begin{lemma}[Alternative definition of weak bisimulation]\label{lem-alternative-weak-bisim} The definition of weak bisimulation given in Definition \ref{def-Weak-bisim} is equivalent to the following one:
+%\end{proof}
+
+\begin{lem}[Alternative definition of weak bisimulation]\label{lem-alternative-weak-bisim} The definition of weak bisimulation given in Definition \ref{def-Weak-bisim} is equivalent to the following one:
 
@@
 
-\end{lemma}
-
-\begin{proof} Note that Definition \ref{def-Weak-bisim} is a particular case of the definition above, thus we only need to prove one direction of the equivalence between the two definitions, namely: \\
+\end{lem}
+
+%\begin{proof}
+\proof Note that Definition \ref{def-Weak-bisim} is a particular case of the definition above, thus we only need to prove one direction of the equivalence between the two definitions, namely: \\
 ($\Rightarrow$) We prove that Definition \ref{def-Weak-bisim} implies the definition above. In other words,
@@
  \displaystyle{\bigvee_{x\in X}} 
-\Big(\forall j\in J.\gamma_j'=\gamma_j \land  \Pred \land \alpha=\alpha''  \land \Pred_{s',x}\subst{\Post_{OT}\uplus\Post\,}\Big)$\\
-\end{proof}
+\Big(\forall j\in J.\gamma_j'=\gamma_j \land  \Pred \land \alpha=\alpha''  \land \Pred_{s',x}\subst{\Post_{OT}\uplus\Post\,}\Big)$
+%\end{proof}
+\qedhere
 
@@
 This section gives decomposition/composition lemmas and their proofs, these are the equivalent of the composition lemmas for open transitions, but applied to weak open automata.
-\begin{lemma}[Weak open transition decomposition]\label{lem-decomposeWOT} 
+\begin{lem}[Weak open transition decomposition]\label{lem-decomposeWOT} 
 	Let $\Leaves(Q)=pLTS_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
@@
 where for any $p$, $\Post_p$ only acts upon  variables $\vars(Q)$.
-\end{lemma}
-
-\begin{proof} Suppose that we have: 
+\end{lem}
+
+%\begin{proof} 
+\proof Suppose that we have: 
 \begin{mathpar}
@@
 %~~\qquad= \Post' \uplus \bigodot_{j=n}^{0} \Post_j $\\
-%\qed
-\end{proof}
-
-\begin{lemma}[Weak open transition composition]\label{lem-Weakcompose1} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
+\qedhere
+%\end{proof}
+
+\begin{lem}[Weak open transition composition]\label{lem-Weakcompose1} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
 	Suppose $j_0\in J$  and:\\[-1ex]
@@
 	\]}
-\end{lemma}
-\begin{proof}
+\end{lem}
+%\begin{proof}
+\proof
 By  Lemma \ref{lem-rel-OT-WOT} we can decompose the WOT of $Q$ into  a series of $k+1$ and $k'+1$ tau open transitions and an $\alpha'_Q$ open transition (observable or not depending on $\alpha_Q$):
@@
 \end{equation*}
-\end{proof}
+%\end{proof}
+\qedhere
 \smallskip
-\begin{lemma}[Weak open transition composition]\label{lem-Weakcompose} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
+\begin{lem}[Weak open transition composition]\label{lem-Weakcompose} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
 Suppose $j_0\in J$ and $\gamma_{j_0}=[\beta_0..\beta_n]$ and additionally:\\[-2ex]
@@
 	\]
-\end{lemma}
-
-\begin{proof} Suppose we have:
+\end{lem}
+
+%\begin{proof} 
+\proof Suppose we have:
 \begin{mathpar}
@@
 This allows us to conclude concerning the lemma. 
-\end{proof}
-
+%\end{proof}
+\qed
 %\newpage
@@
 %\end{theorem}
- \begin{proof}  Consider $Q$ weak FH-bisimilar to $Q'$.
+% \begin{proof}
+\proof  Consider $Q$ weak FH-bisimilar to $Q'$.
 It means that there exists an FH-bisimulation $\mathcal{R}_{Q,Q'}$ relating the two pNets $Q$ and $Q'$.
@@
 \end{multline*}
-We conclude by observing that $\Post_P$ has no effect on variables of $Q$ and $Q'$, and thus on $\Pred_{Q,Q' x}$
+We conclude by observing that $\Post_P$ has no effect on variables of $Q$ and $Q'$, and thus on $\Pred_{Q,Q' x}$.
+\qed
 % OLD
@@
 %	\]
- \end{proof}
+% \end{proof}
 
@@
 
- \begin{proof}   Consider $P$ weak FH-bisimilar to $P'$.
+% \begin{proof} 
+\proof  Consider $P$ weak FH-bisimilar to $P'$.
 There exists an FH-bisimulation $\mathcal{R}_{P,P'}$ relating $P$ and $P'$.
@@
 We conclude by observing that $\Post_Q$ has no effect on variables of $P$ and $P'$, and thus on $\Pred_{P,P' x}$ and $\Pred$ leading to the conclusion about $\alpha_Q=\beta$.
-\end{proof}
+\qed %\end{proof}
 

### 2021-10-22 2016-Weak-FH-Bisim/2021-09-letter2Reviewers.tex
typos and lmcs style
small typos

--- 2021-10-19 2016-Weak-FH-Bisim/2021-09-letter2Reviewers.tex
@@
 
-\item We added an example illustrating the difference between our weak bisimulation and weak bisimulation for CCS (more generaly for a process algebra with a choice operator and a $\tau$ action)
+\item We added an example illustrating the difference between our weak bisimulation and weak bisimulation for CCS (more generally for a process algebra with a choice operator and a $\tau$ action).
 
-\item We improved explanations wherever the reviewers indicated it was necessary (e.g.  semantics of pNets,  definition of bisimulation, definition of weak open transitions)
+\item We improved explanations wherever the reviewers indicated it was necessary (e.g.  semantics of pNets,  definition of bisimulation, definition of weak open transitions).
 
@@
 
-- I was left unconvinced that using open automata as an intermediary structure to define the bisimualtion relations is the best approach to develop this material.
+- I was left unconvinced that using open automata as an intermediary structure to define the bisimulation relations is the best approach to develop this material.
 The authors should give more convincing argument that such definitions could not be adequately defined directly on pNets (an already complex framework).
@@
 
-- In general, weak bisimulation is *not* a congruence for all types of interacting contexts.  For instance, in the case of CCS, the classsical counter example is that whereas 
+- In general, weak bisimulation is *not* a congruence for all types of interacting contexts.  For instance, in the case of CCS, the classical counter example is that whereas 
 tau.a.0  \\bisim  a.0

### 2021-10-22 2016-Weak-FH-Bisim/2021-09-letter2Reviewers.tex

@@
 address in a straightforward manner. Major points of the reviews have not been omitted in 
-any case.
+any case. We additionally attach a version of the paper highlighting all the changes we made.
 

### 2021-10-22 2016-Weak-FH-Bisim/WeakBisim.tex

@@
 
-\begin{definition}[pLTS]
+\begin{defi}[pLTS]
 \label{pLTS}
@@
 \end{itemize}
-\end{definition}
+\end{defi}
 
@@
 
-\begin{definition}[pNets]\label{def-pnets}
+\begin{defi}[pNets]\label{def-pnets}
 A pNet $\pNet$ is a hierarchical structure where leaves are pLTSs and holes\\
@@
 action terms.
-\end{definition}
+\end{defi}
 
@@
 
-\begin{definition}[Sorts, Holes, Leaves, Variables of pNets]\label{def-sortholeleave}~~
+\begin{defi}[Sorts, Holes, Leaves, Variables of pNets]\label{def-sortholeleave}~~
 
@@
 }
-\end{definition}
+\end{defi}
 
@@
 
-\begin{definition}[pNet composition]
+\begin{defi}[pNet composition]
 	An open pNet: $\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
@@
 	\]
-\end{definition}
+\end{defi}
 
@@
 %notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
-\begin{definition}[Open transitions]\label{def:OT}
+\begin{defi}[Open transitions]\label{def:OT}
 	\label{def:OpenTransitions}
@@
         modulo logical equivalence on their predicate. 
-\end{definition}
+\end{defi}
 
@@
 An open automaton is  an automaton where each transition is an open transition.
-\begin{definition}[Open automaton]
+\begin{defi}[Open automaton]
 	\label{def:open-automaton}
@@
 \end{mathpar}
-\end{definition}
+\end{defi}
 
@@
 Indeed the standard notation would be too heavy in our case.}:
- \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim} ~\\
+ \begin{defi}[Strong FH-bisimulation]\label{def-FH-bisim} ~\\
 \noindent
@@
 % \TODO{do we want formulas for this?}
- \end{definition}
+ \end{defi}
 Classically, $\Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}$
@@
 states from other tuples.
-\begin{definition}[States of open pNets]\label{def-states}
+\begin{defi}[States of open pNets]\label{def-states}
   A state of an open pNet is a tuple (not necessarily finite) of the
@@
 $InitState(\pNet) = \triangleleft {{s_i}_0}^{i\in L}  \triangleright$.
-\end{definition}
+\end{defi}
 To be precise, the state of each pLTS is entirely characterized by both the state of the automaton, and the value of its variables $V$.
@@
 
-\begin{definition}[Semantics of open pNets]
+\begin{defi}[Semantics of open pNets]
 	\label{def:operationalSemantics} The semantics of a pNet $\pNet$ is an open automaton $A\!= 
@@
 	%%include it, because it may change the decidability conditions on predicates}
-\end{definition}
+\end{defi}
         	A key to understand this rule is that the open transitions are
@@
 	strong (symbolic) bisimulation on automata to open pNets.
-\begin{definition}[FH-bisimulation for open pNets]\label{def:bisim-pnets}
+\begin{defi}[FH-bisimulation for open pNets]\label{def:bisim-pnets}
 Two pNets are FH-bisimilar if there exists a relation between their associated 
@@
 %\TODO{check}
-\end{definition}
+\end{defi}
 %\TODO{Predicate=True me pose un probleme...
@@
 We define $\Id(V)$ as the identity function on the set of variables $V$.
-\begin{definition}[Non-observability of $\tau$ actions for open automata]\label{def:Non-ObsTau}
+\begin{defi}[Non-observability of $\tau$ actions for open automata]\label{def:Non-ObsTau}
 An open automaton $A = \mylangle J,\mathcal{S},s_0,V,\mathcal{T}\myrangle$ \emph{cannot observe $\tau$ actions} if and only if for all $j$ in $J$ and $s$ in $\mathcal{S}$ we have:
@@
 \end{enumerate}
-\end{definition}
+\end{defi}
 The first statement of the definition states that the open automaton must allow a hole to do a silent action at any time, and must not observe it, i.e.
@@
 
-\begin{definition}[Weak open transition (WOT)]\label{def:weakOT}
+\begin{defi}[Weak open transition (WOT)]\label{def:weakOT}
 A weak open transition over a
@@
 A weak open automaton $\mylangle J,\mathcal{S},s_0,V,\WT\myrangle$ is similar to an open automaton  except that $\WT$ is a set of weak open transitions over $J$ and $\mathcal{S}$.
-\end{definition}
+\end{defi}
 
@@
 This is done in a way that resembles the process of $\tau$ saturation: we add  $\tau$ open transitions before or after another (observable or not) open transition.
-\begin{definition}[Building a weak open automaton]\label{def:buildweakOT}
+\begin{defi}[Building a weak open automaton]\label{def:buildweakOT}
   Let $A = \mylangle J,\mathcal{S},s_0,V,\mathcal{T}\myrangle$ be an open automaton. 
@@
 
-\end{definition}
+\end{defi}
 Rule $\WTUn$ states that it is always possible to do a non-observable transition, where the state is unchanged and the holes perform no action.
@@
 
-\begin{definition}[Weak FH-bisimulation]\label{def-Weak-bisim} ~\\
+\begin{defi}[Weak FH-bisimulation]\label{def-Weak-bisim} ~\\
 \noindent
@@
 the predicate associated to the relation between the initial states is \True.
- \end{definition}
+ \end{defi}
 
@@
 
-\begin{definition}[Non-observability of silent actions for pNets]\label{def:non-obspNet}~\\
+\begin{defi}[Non-observability of silent actions for pNets]\label{def:non-obspNet}~\\
 A pNet $\mylangle \pNet_i^{i\in I} , \Sort_j^{j\in J}, \set{\symb{SV}}\myrangle$
@@
 \end{equation*}
-\end{definition}
+\end{defi}
 
@@
 
-\begin{definition}[Semantics of pNets as a weak open automaton]
+\begin{defi}[Semantics of pNets as a weak open automaton]
 Let $A$ be the open automaton expressing the semantics of an open pNet $\pNet$; let $\mylangle J,\mathcal{S},s_0, V, \WT\myrangle$ be the weak open automaton derived from $A$; we call this weak open automaton the weak semantics of the pNet $\pNet$.
 Then, we denote $\pNet \models \WOT$ whenever $\WOT\in\WT$.
-\end{definition}
+\end{defi}
 

### 2021-10-25 SujetStage/2021-pNetsubjectM2.tex
version v0

--- 2020-10-20 SujetStage/2020-pNetsubjectM2.tex
@@
 \\\bigskip
-\resizebox{\textwidth}{!}{\bf Refinement for open automata}
+\resizebox{\textwidth}{!}{\bf Session Types meet Open Automata}
 %  Systolisation d'un réseau de processus polyédrique}
@@
 \begin{description}
-\item[\bf Main advisor:] Rabéa Ameur-Boulifa 
-\item[\bf Co-advisors:] Ludovic Henrio and Eric Madelaine
+\item[\bf Main advisor:] Rabéa Ameur-Boulifa ?
+\item[\bf Co-advisors:] Ludovic Henrio and Eric Madelaine?
 \item[\bf Place:] Eurecom  -- Sophia Antipolis
@@
 
-Establishing equivalences or refinement relations between programs or system is crucial  for verifying correctness of programs, by establishing that one implementation is the refinement of a specification.
+In the previous years, we have studied theoretical foundations for open
+systems and we defined  open automata \cite{arxiv-weakbisim,henrio:Forte2016,hou:hal-02406098} that can be seen as labelled transition systems (LTSs) with parameters and holes. The transitions of open
+automata are much more complex than transitions of an LTS as the ﬁring on a transition depends on parameters and actions that are symbolic.
 
-In the previous years, we have studied theoretical foundations for open
-systems and our formalism, called open automata, is able to represent operators of composition of processes,  represented
-as hierarchically composed automata with holes and parameters. 
-Our long 
-term goal is to 
-develop a methodology combining symbolic operational semantic and bisimulation 
-equivalences with deductive reasoning on the data part, 
-and in practice combining bisimulation algorithms with SMT solvers to get automatic 
-procedures proving equational properties
-of these open systems.
-In the last years, we designed a weak bisimulation theory for  open automata and a translation from a specification language that we used, called pNets, to open automata~\cite{arxiv-weakbisim,henrio:Forte2016,hou:hal-02406098}.
+Establishing  whether two open automata are composable or not require the designer to provide the behaviour of all holes in a context where they are used; which consists in describing all the interactions and the series of inputs and outputs of data exchanged  between the automata.
+To make this task reusable by other designers, we are interested in characterising  the behavioural condition that must be satisfied by a process that would be plugged into a hole to satisfy the composability condition.
 
-Among the properties of our formalisms, we are interested in compositionality: If two systems are proven equivalent they will be undistinguishable by their context, and they will also be undistinguishable when their holes are filled with equivalent systems.
-The article \cite{arxiv-weakbisim} is illustrated with a transport protocol running example; it shows the characteristics of our formalism and our bisimulation relations.
+To tackle this issue, we ask: Can we synthesise a global type from a collection of automata so as to ensure the composability of an open automaton whose hole is compatible with this global type?
 
@@
 
-The main objective of the internship is to study refinement theory for open automata.  
-Our purpose is to define a refinement relation between the symbolic models allowing refinement verification for a class of open systems.
+The main objective of the internship  deals with the characterization of dynamic execution of open automata as behavioural types.
+Our purpose is to define the composability condition of two open automata.
 
-The internship will start with a study of the semantics of a simple language called value passing CCS.
-The first objective of this internship is to design a semantics value passing CCS in terms of open automata.
-Especially, we will be able to extend the semantics by taking into account the semantics of operators for composing CCS processes.
-
-After this preliminary step, the next objective will be to design a refinement theory for open automata.
-We will make sure that this relation is specified in a constructive manner, so that an algorithm could be derived from the specification in the future~\cite{Bellegarde:MEMOCODE2003}.
-The relationship between refinement and automata composition should also play a major role in this definition.
-
-%The purpose is to define the refinement semantics as a relation between open automata that can be classified in  and we will make sure that an algorithm could be designed to verify refinement can also be verified for finite state systems using an algorithmic method.
-
-The next steps in the internship will rely on these two initial works; they will consist in addressing some of the following (independent) objectives:
-\begin{itemize}
-\item Express and prove compositionality properties for the refinement relation over open automata.
-\item Study formally the behaviour of CCS operators wrt refinement.
-\item Compare this theory with the state of the art of the refinement semantics.
-\item Design the algorithm that checks refinement between two open automata.
-\end{itemize}
+The internship will start with a study of the semantics of  open automata and the notion behavioural types \cite{Hans:2016}, in particular the notion of session types that allows to describe the dynamic aspects of processes.
 
@@
 
-\bibitem{Bellegarde:MEMOCODE2003}
-Fran{\c{c}}oise Bellegarde, Celina Charlet and Olga Kouchnarenko:
-\newblock {How to Compute the Refinement Relation for Parameterized Systems}.
-\newblock 1st {ACM} {\&} {IEEE} International Conference on Formal Methods and Models for Co-Design {(MEMOCODE} 2003), 24-26 June 2003, Mont Saint-Michel, France. 
-\newblock DOI: 10.1109/MEMCOD.2003.1210095
+\bibitem{Hans:2016}
+Hans H\"uttel, Ivan Lanese, Vasco T.
+Vasconcelos, Lu\`is Caires, Marco Carbone, Pierre-Malo Deni\'elou, Dimitris Mostrous, Luca Padovani, Ant\`onio Ravara, Emilio Tuosto, Hugo Torres Vieira, Gianluigi Zavattaro:
+\newblock {Foundations of Session Types and Behavioural Contracts}.
+\newblock ACM Comput. Surv. 49(1): 3:1-3:36 (2016)
 

### 2021-10-26 SujetStage/2021-pNetsubjectM2.tex
version v1

@@
 systems and we defined  open automata \cite{arxiv-weakbisim,henrio:Forte2016,hou:hal-02406098} that can be seen as labelled transition systems (LTSs) with parameters and holes. The transitions of open
-automata are much more complex than transitions of an LTS as the ﬁring on a transition depends on parameters and actions that are symbolic.
+automata are much more complex than transitions of an LTS as the firing on a transition depends on parameters and actions that are symbolic.
 
-Establishing  whether two open automata are composable or not require the designer to provide the behaviour of all holes in a context where they are used; which consists in describing all the interactions and the series of inputs and outputs of data exchanged  between the automata.
-To make this task reusable by other designers, we are interested in characterising  the behavioural condition that must be satisfied by a process that would be plugged into a hole to satisfy the composability condition.
+Establishing  whether two open automata are equivalent  or not requires the designer to provide the behaviour of all holes in a context where they are used; which consists in describing all the interactions and the series of inputs and outputs of data exchanged  between the automata and its environment.
+To make those reusable, we are interested in enriching holes with description of behaviours to give them enough power and enable us to check equivalences for these open systems.
+The description will characterise the assumptions that the automaton makes about the behavior of its surroundings  in order to guarantee certain conditions.
 
-To tackle this issue, we ask: Can we synthesise a global type from a collection of automata so as to ensure the composability of an open automaton whose hole is compatible with this global type?
+To tackle this issue, we ask: { \it Can we synthesise a global type from a collection of automata so as to ensure the composability of an open automaton  with compatible  surrounding automaton? }
 
@@
 
-The main objective of the internship  deals with the characterization of dynamic execution of open automata as behavioural types.
-Our purpose is to define the composability condition of two open automata.
+The main objective of the intern ship  deals with the characterization of interactions  of open automaton with its environment as behavioural types.
+More specifically, the intern ship would follow the following steps:
+\begin{itemize}
+\item The internship will start with a familiarization with technical material: the semantics of  open automata and the notion behavioural types \cite{Hans:2016}, in particular the notion of session types that allows to describe the dynamic aspects of processes.
 
-The internship will start with a study of the semantics of  open automata and the notion behavioural types \cite{Hans:2016}, in particular the notion of session types that allows to describe the dynamic aspects of processes.
+\item Design of an adequate characterisation of  compatibility condition  suitable for the composition open automata, and which is sufficient to decide if two open automata are compatible or not. 
+\item Examples/Algorithm
+
+\end{itemize}
 

### 2021-10-26 SujetStage/2021-pNetsubjectM2.tex
sujet de stage

@@
 
-To tackle this issue, we ask: { \it Can we synthesise a global type from a collection of automata so as to ensure the composability of an open automaton  with compatible  surrounding automaton? }
+To tackle this issue, we ask: { \it Can we synthesise a global type from a collection of automata so as to ensure the composability of an open automaton  with a compatible  surrounding automaton? }
 
@@
 
-The main objective of the intern ship  deals with the characterization of interactions  of open automaton with its environment as behavioural types.
-More specifically, the intern ship would follow the following steps:
+The main objective of the internship is to deal with the characterization of interactions  of open automaton with its environment. These interactions can be characterised as behavioural types.
+More specifically, the internship would follow the following steps:
 \begin{itemize}
-\item The internship will start with a familiarization with technical material: the semantics of  open automata and the notion behavioural types \cite{Hans:2016}, in particular the notion of session types that allows to describe the dynamic aspects of processes.
+\item Familiarization with technical material: the semantics of  open automata and the notion behavioural types \cite{Hans:2016} that allows to describe the dynamic aspects of processes.
+In particular the notion of session types that focus on process interactions should be studied.
 
 \item Design of an adequate characterisation of  compatibility condition  suitable for the composition open automata, and which is sufficient to decide if two open automata are compatible or not.
+
+\item Application to the proof of absence of deadlock upon composition.
+
+\item  We additionally have defined a notion of refinement between open automata that would benefit from such behavioural types.
+One additional objective of the internship could be to improve the definition of refinement based on the notion of behavioural types that has been defined in the previous steps.
+
 \item Examples/Algorithm

### 2021-10-27 SujetStage/2021-pNetsubjectM2.tex
explications de "holes and parameters"

@@
 systems and we defined  open automata \cite{arxiv-weakbisim,henrio:Forte2016,hou:hal-02406098} that can be seen as labelled transition systems (LTSs) with parameters and holes. The transitions of open
-automata are much more complex than transitions of an LTS as the firing on a transition depends on parameters and actions that are symbolic.
+automata are much more complex than transitions of an LTS: they include guards expressing the relations between the parameters of the automaton with the actions of the holes, and assignments encoding their effects.
+% as the firing on a transition depends on parameters and actions that are symbolic.
+Holes here are modeling the environment of the open automaton, that can be used to compose open automata together to build bigger systems. We proved that our models 
+have good properties, namely that composition preserves some classes of equivalences.
 

### 2021-10-27 SujetStage/2021-pNetsubjectM2.tex
version v2

@@
 \\\bigskip
-\resizebox{\textwidth}{!}{\bf Session Types meet Open Automata}
+\resizebox{\textwidth}{!}{\bf Open Automata meet Session Types}
 %  Systolisation d'un réseau de processus polyédrique}
@@
 
-Establishing  whether two open automata are equivalent  or not requires the designer to provide the behaviour of all holes in a context where they are used; which consists in describing all the interactions and the series of inputs and outputs of data exchanged  between the automata and its environment.
-To make those reusable, we are interested in enriching holes with description of behaviours to give them enough power and enable us to check equivalences for these open systems.
-The description will characterise the assumptions that the automaton makes about the behavior of its surroundings  in order to guarantee certain conditions.
+The composition of open automata refers to filling holes, it requires to check the compatibility of their sorts.
+Nowadays, we simply say that two open automata are compatible if they consist of the same actions with the same arity.
+But,
+ we are interested in enriching holes with description of behaviours to give them enough power and enable us to check equivalences for these open systems. The description will characterise all the
+interactions and the series of inputs and outputs of data exchanged between the automata and its surroundings.
+Precisely, the theory of session types and behavioural types  \cite{Fantechi:MLTCDP2019} are intended  to describe dynamic aspects of the behaviour of processes.
 
-To tackle this issue, we ask: { \it Can we synthesise a global type from a collection of automata so as to ensure the composability of an open automaton  with a compatible  surrounding automaton? }
+To tackle this issue, we ask: { \it Can we synthesise a global type from a collection of automata in order to ensure the composability of an open automaton  with a compatible  surrounding automaton? }
 
@@
 
-\item Design of an adequate characterisation of  compatibility condition  suitable for the composition open automata, and which is sufficient to decide if two open automata are compatible or not.
+\item Design of an adequate characterisation of  compatibility condition  suitable for the composition open automata, and study the guarantees brought by this condition.
 
@@
 
-\item Examples/Algorithm
+\item Design of examples demonstrating the benefit of this work.
 
@@
 
+\bibitem{Fantechi:MLTCDP2019}
+Alessandro Fantechi, Elie Najm, Jean-Bernard Stefani:
+\newblock {From Behavioural Contracts to Session Types}.
+\newblock Models, Languages, and Tools for Concurrent and Distributed Programming 2019: 278-297
+
 \bibitem{hou:hal-02406098}

### 2021-10-29 SujetStage/2021-pNetsubjectM2.tex
une petite passe pour preciser les choses

@@
 % as the firing on a transition depends on parameters and actions that are symbolic.
-Holes here are modeling the environment of the open automaton, that can be used to compose open automata together to build bigger systems. We proved that our models 
-have good properties, namely that composition preserves some classes of equivalences.
+ We proved that our models 
+have good properties, namely that composition preserves some properties like bisimulation.
 
 The composition of open automata refers to filling holes, it requires to check the compatibility of their sorts.
-Nowadays, we simply say that two open automata are compatible if they consist of the same actions with the same arity.
+Nowadays, we simply verify the compatibility of two automata to be composed based on   action labels and  arity.
 But,

### 2021-11-04 2021-Refinement/paper/refinementarticle.tex
vars in ots

@@
 
-\usepackage{tikz}
+\usepackage{tikz,mathpartir}
 
@@
 
-We first: introduce open automata (NOT NEW), their composition, and the deadlock-free composition.
+We first: introduce open automata (NOT NEW), their composition, 
+and the deadlock-free composition.
 
@@
 
-- a first relation that focuses on the automaton part and a second that deals partially with open behaviour
+- a first relation that focuses on the automaton part 
+and a second that deals with open behaviour
 
-we will see that having at the same time composition and transitivity also raises challenges; we introduce a relation that addresses this challenge.
+we will see that having at the same time composition and transitivity also raises challenges; we introduce a new form of refinement relation that addresses this challenge.
 
@@
 
-The notion of refinement aims of capturing the relation between  a specification and an implementation of the same component.
+The notion of refinement aims captures the relation between  a specification and an implementation of the same component.
 It is usually defined as trace inclusion or simulation \cite{Milner:1980, Kouchnarenko:2007}; this ensures that all behaviours of the implementation must be also behaviours of the specification.
@@
 An \emph{open transition} is a tuple \nmm{\OTg} with \(s, s' \in S\) the source and target states, \(\alpha \in \actions\) the produced action, \(J' \subseteq J\) the holes involved in the transition, \(\beta_j \in \actions\) the actions of the holes, \(g \in \formulas\) the guard and \(\psi: V \to \terms\) the variable assignments.
+To be well-formed, an open transition should use only variables of the automaton and variables appearing in the involved actions, formally: 
+\begin{align*}
+\fvars(g)&\subseteq \fvars(\alpha)\cup \bigcup_{j \in J'} \fvars{\beta_j} \cup V \\ \forall v\in V.\, \fvars(\psi(v))&\subseteq \fvars(\alpha)\cup \bigcup_{j \in J'} \fvars{\beta_j} \cup V
+\end{align*}
 \end{definition}
@@
 \vspace{-1cm}
-\begin{gather*}
-	\fguard{\OTg} = g \\
-	\fvars{\OTg} = \mpar{\fvars{\alpha} \cup \fvars{g} \cup \bigcup_{j \in J'} \fvars{\beta_j} \cup \bigcup_{v \in V} \fvars{\psi\mpar{v}}} \setminus V
-\end{gather*}
+\begin{mathpar}
+	\fguard{\OTg} \!=\! g \qquad
+	\fvars{\OTg} \!=\! \mpar{\fvars{\alpha}  \cup \bigcup_{j \in J'} \!\fvars{\beta_j} } \setminus V
+\end{mathpar}
 \end{definition}
@@
 \end{definition}
-Again we use guards to characterise that the transition occurs.
-It is not sufficient to ensure the existence of equivalent transitions in general, but it will be sufficient in the context of refinement.
+Again we use guards to ensure that the transition can occur. It is not sufficient to ensure the existence of equivalent transitions in general, but it will be sufficient in the context of refinement.
 

### 2021-11-04 2021-Refinement/paper/refinementarticle.tex
removed def 9

@@
 \begin{align*}
-\fvars(g)&\subseteq \fvars(\alpha)\cup \bigcup_{j \in J'} \fvars{\beta_j} \cup V \\ \forall v\in V.\, \fvars(\psi(v))&\subseteq \fvars(\alpha)\cup \bigcup_{j \in J'} \fvars{\beta_j} \cup V
+\fvars{g}&\subseteq \fvars{\alpha}\cup \bigcup_{j \in J'} \fvars{\beta_j} \cup V \\ \forall v\in V.\, \fvars{\psi(v)}&\subseteq \fvars{\alpha}\cup \bigcup_{j \in J'} \fvars{\beta_j} \cup V
 \end{align*}
@@
 Refinement through composition  leads to a model in which composition can be used both to add new holes to a system and to fill holes, obtaining a system with less holes.
-Next section will identify a refinement relation with the possibility to have different holes in the compared automata.\\
-
-\TODO{Je ne suis pas sure que la def precedente soit correcte: il faut ajouter la notion de  configuration comme suit:}
-
-\begin{definition}[Hole-equal simulation]
-Consider two OAs \(\OAg[1]\) and \(\OAg[2]\) with  \(J_1 = J_2\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $S_1$ to $S_2$ if the following conditions hold:
-\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
-\item[(2)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)\vspace{-8pt}
-\noindent\begin{multline*}
-\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} t_1 = \OTx{1}{}{1}{1} \in \fOT{s_1},  \forall \sigma: V_1 \uplus V_2 \uplus \fvars{t_1} \to \values,\\
-\bigsymb{\exists} \mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}\!\!\!\!, 
-	\exists \sigma':\biguplus_\subbox{t_{2x} \in \fOT{s_2}} \fvars{t_{2x}}   \to \values\\
-		   \mpar{\forall x \in X, J'_{2x}= J'_1} \\[-2pt]
-%		\nwedge  
-		\left( \sigma  \vdash  R\mpar{s_1, s_2} \wedge g_1 \implies \sigma \uplus \sigma' \vdash \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x}} \beta_{1j} = \beta_{2xj} \nwedge \\[12pt]
-			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}}\right)
-	\end{array} 
-%\\
-%	\wedge \mpar{V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
-\end{multline*}
-\item[(3)] $R$ is deadlock reducing.
-\end{definition}
+Next section will identify a refinement relation with the possibility to have different holes in the compared automata.
 
 %Technically,  it expresses how the concepts from the abstract and the refined systems are linked together.
+
+\TODO{add an example}
+
+\TODO{refer to properties of section 6} We will show in Section~\ref{sec:prop} that this refinement relation has god properties in terms of transitivity, compositionality, reflexivity, etc.
 

### 2021-11-04 2021-Refinement/paper/refinementarticle.tex
nicer defs
organisatino and lemmas

@@
 \everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} t_1 = \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
-		\quad \mpar{\forall x \in X, J'_{2x}= J'_1} \\[-2pt]
-		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash \left( R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+		\bigsymb{\forall} t_1 = \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\[10pt]
+		\quad \mpar{\forall x \in X, J'_{2x}= J'_1} \\[2pt]
+		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\
+\hspace{5em} \left( R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
 			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x}} \beta_{1j} = \beta_{2xj} \\[12pt]
@@
 In practice, when performing successive refinements, we  keep track of which holes are in common at each step of refinement.
+
+\TODO{say explicitly what is the difference in the formalisation compared to previous def}
 \begin{definition}[Open automata refinement]\label{Def:OA-Refinement}
-For two open automata \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a refinement of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a deadlock reducing relation $R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that:
- \[\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}}\]
-and
+For two open automata \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a refinement of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a relation $R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that:
+\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
+\item[(2)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)
 \begin{multline*}
- \forall \mpar{s_1, s_2} \in S_1 \times S_2, \\
 	\everymath{\displaystyle}\begin{array}{l}
 		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\[12pt]
-		\quad \mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H} \\[-1pt]
-		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash \mpar{R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+		\quad \mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H} \\[1pt]
+		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\\hspace{5em} \mpar{R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
 			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \\
 			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}}} \\
-	\end{array} \\
+		\end{array}}} 
+	\end{array} 
 \end{multline*}
+\item[(3)] $R$ is deadlock reducing.
 
@@
 It is easy to see that the hole-equal simulation is a particular case of open automata refinement, when  $J_1=J_2=H$.
+
+\TODO{example}
 
@@
 
-- composition is a refinement (under which condition?)
+\begin{theorem}[Transitivity]
+If $\wrel{A_1}{A_2}{H}$ and $\wrel{A_2}{A_3}{H}'$, then $\wrel{A_1}{A_3}{H\cap H'}$.
+\end{theorem}
+\TODO{proof in appendix + proof sketch}
+
+- composition is a refinement (under which condition? non-locking composition?)
 
@@
 
+\appendix
+\section{Proof of transitivity}
+\begin{quote}
+If $\wrel{A_1}{A_2}{H}$ and $\wrel{A_2}{A_3}{H}'$, then $\wrel{A_1}{A_3}{H\cap H'}$.
+
+\end{quote}
+
  \bibliographystyle{splncs04}

### 2021-11-17 2021-Refinement/paper/refinementarticle.tex
debut proof transitiv.

@@
 \begin{quote}
-If $\wrel{A_1}{A_2}{H}$ and $\wrel{A_2}{A_3}{H}'$, then $\wrel{A_1}{A_3}{H\cap H'}$.
+If $\wrel{A_1}{A_2}{H}$ and $\wrel{A_2}{A_3}{H'}$, then $\wrel{A_1}{A_3}{H\cap H'}$.
+\end{quote}
 
-\end{quote}
+\proof We consider different cases:
+\begin{enumerate}
+\item One has to prove it first initial configurations. We have:
+\begin{align*}
+\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar
+{\sigma_{02} \uplus \sigma_{03} \vdash R_{23}\mpar{s_{02}, s_{03}}}
+\implies
+\end{align*}
+\TODO{I will continue}
+\item For any open transition $t_1$ in $T_1$  originating from $s_1$:
+\begin{align*}
+\OTx{1}{}{1}{1} \in \fOT{s_1}
+\end{align*}
+there exist an indexed family of OTs originating from $s_2$: 
+\begin{align*}
+\mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X} \subseteq T_2
+\end{align*}
+such that $\mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H}$ and
+\begin{multline*}
+%\everymath{\displaystyle}
+V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\ \mpar{R_{12}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \\
+			\nwedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}}} 
+\end{multline*}		
+\medskip
+
+For any open transition $t_{2x}$ in $T_2$, since  originating from $s_2$:
+\begin{align*}
+\OTx{2}{x}{2x}{2x} \in \fOT{s_2}
+\end{align*}
+there exist an indexed family of OTs originating from $s_3$: 
+\begin{align*}
+\mpar{\OTx{3}{xy}{2xy}{2xy} \in \fOT{s_3}}^{y \in Y} \subseteq T_3
+\end{align*}
+such that $\mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H}$ and
+\begin{multline*}
+\everymath{\displaystyle}
+V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\\hspace{5em} \mpar{R_{23}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \\
+			\nwedge g_{2x} \wedge R_{23}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}}} 
+\end{multline*}
+
+ $\wrel{A_1}{A_2}{H}$, there is a relation $R_{12}$
+\begin{multline*}
+	\everymath{\displaystyle}\begin{array}{l}
+		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\[12pt]
+		\quad \mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H} \\[1pt]
+		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\\hspace{5em} \mpar{R_{12}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \\
+			\nwedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}}} 
+	\end{array} 
+\end{multline*}
+
+\end{enumerate}
 

### 2021-12-02 2021-Refinement/paper/refinementarticle.tex
proof in progress

--- 2021-11-04 2021-Refinement/paper/refinementarticle.tex
@@
 
-perhaps say that one of the automaton is expected to be the reinement of the other BUT the def is not dependent on the notion of refinement
+perhaps say that one of the automaton is expected to be the refinement of the other BUT the def is not dependent on the notion of refinement
 
@@
 
-Next definition is not intuitive, it does not say much because it says that if t2 is not in a deldlock position then t1 can do a transition but not necessarily with the same input values.
+Next definition is not intuitive, it does not say much because it says that if t2 is not in a deadlock position then t1 can do a transition but not necessarily with the same input values.
 This is very weak but sufficient when composed with the def  of simulation.
@@
 \begin{quote}
-If $\wrel{A_1}{A_2}{H}$ and $\wrel{A_2}{A_3}{H}'$, then $\wrel{A_1}{A_3}{H\cap H'}$.
+If $\wrel{A_1}{A_2}{H}$ and $\wrel{A_2}{A_3}{H'}$, then $\wrel{A_1}{A_3}{H\cap H'}$.
+\end{quote}
+\proof 
+Suppose we have $R_{12}$ a relation between states
+of $A_1$ and of $A_2$;  Suppose we also have $R_{23}$ a relation between states of $A_2$ and of $A_3$. We build a relation between
+ states of $A_1$ and of $A_3$ as follows:  for each pair of states $s_1$, $s_3$, for each state $s_2$ such that $R_{12}$ relates $s_1$ and $s_2$, and $R_{23}$ relates $s_2$ and $s_3$.
+Let $R_{13}$ be the relation:\\
+  $R_{13}=\{(s_1,s_3) \in S_1\times S_2 | (s_1,s_2) \in R_{12}\wedge (s_2,s_3) \in R_{23} \} $
 
-\end{quote}
+We will show that ($R_{13}$, $H\cap H'$) is a hole-tracking simulation of $A_1$ by  $A_3$.
+
+Consider each condition of the definition of a refinement of open automata.
+\begin{enumerate}
+\item One has to prove it first initial configurations.
+By knowing that substitutions only have an effect on the variables of the open automaton they belong to, they also produce terms containing only variables of the open automaton they belong to.
+We have:
+\begin{multline*}
+\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar
+{\sigma_{02} \uplus \sigma_{03} \vdash R_{23}\mpar{s_{02}, s_{03}}}\implies\\
+R_{12}\mpar{s_{01},s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02}} \wedge R_{23}\mpar{s_{02}, s_{03}}\psubst{\sigma_{02} \uplus \sigma_{03}}\implies\\
+R_{12}\mpar{s_{01},s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} \wedge R_{23}\mpar{s_{02}, s_{03}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}}\implies\\ \underbrace{R_{12}\mpar{s_{01},s_{02}}\wedge R_{23}\mpar{s_{02}, s_{03}}}_{R_{13} \mpar{s_{01}, s_{03}}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} \implies\\
+\sigma_{01} \uplus \sigma_{03} \vdash R_{13} \mpar{s_{01}, s_{03}}
+\end{multline*}
+
+\item Consider $\mpar{s_{1}, s_{3}} \in R_{13}$ then there is a set of states of $A_2$ relating  $s_{1}$ and $s_{3}$, let $(t_x)^{x\in X}$ be the family of transition originating from  these states:
+\[R_{13}=\bigcup_{\begin{array}{c}       		
+       			\mpar{s_1,s_{2x}} \in R_{12}\\
+\mpar{s_{2x},s_3}\in R_{23}
+       		\end{array}
+}R_{12}\mpar{s_1,s_{2x}} \wedge R_{23}\mpar{s_{2x},s_3} \]
+
+On one side, we have for any open transition $t_1$ in $T_1$  originating from $s_1$:
+\begin{align*}
+\OTx{1}{}{1}{1} \in \fOT{s_1}
+\end{align*}
+there exist an indexed family of OTs originating from $s_2$: 
+\begin{align*}
+\mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X} \subseteq T_2
+\end{align*}
+such that $\forall x \in X, J'_{2x} \cap H = J'_1 \cap H$ and
+\begin{multline*}
+%\everymath{\displaystyle}
+V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\ \mpar{R_{12}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \\
+			\nwedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}}} 
+\end{multline*}		
+that can be re-written:
+\begin{multline*}
+%\everymath{\displaystyle}
+\forall v \in \mpar{\fvars{\alpha_{2x}}  \cup \bigcup_{j \in J'} \!\fvars{\beta_{2jx}}} \setminus \mpar{V_1 \uplus V_2 \uplus \fvars{t_1}}, \\ \mpar{R_{12}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2jx} \\
+			\nwedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}}} \\
+	\end{multline*}	
+\medskip
+Multiplying the two terms of the implication by $R_{23}\mpar{s_2,s_3}$ we get:
+
+\begin{multline*}
+ \mpar{R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2,s_3} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2jx} \nwedge\\
+			R_{23}\mpar{s_2,s_3}\wedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}}} \\
+	\end{multline*}
+
+On the other side, from the relation between $A_2$ and $A_3$ we have for any open transition $t_{2x}$ in $T_2$ originating from $s_2$:
+\begin{align*}
+\OTx{2}{x}{2x}{2x} \in \fOT{s_2}
+\end{align*}
+there exist an indexed family of OTs originating from $s_3$: 
+\begin{align*}
+\mpar{\OTx{3}{xy}{3xy}{3xy} \in \fOT{s_3}}^{y \in Y} \subseteq T_3
+\end{align*}
+such that $\forall y \in Y, J'_{2x} \cap H' = J'_{3xy} \cap H'$ and
+\begin{multline*}
+\everymath{\displaystyle}
+V_2 \uplus V_3 \uplus \fvars{t_{2x}} \vdash\\\hspace{2em} \mpar{R_{23}\mpar{s_2, s_{3}} \wedge g_{2x} \implies \operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			 \alpha_{2x}=\alpha_{3xy} \wedge \bigwedge_\subbox{j \in J'_{3xy} \cap H'} \beta_{2jx}=\beta_{3jxy} \\
+			\nwedge g_{3xy} \wedge R_{23}\mpar{s'_{2x}, s'_{3xy}}\psubst{\psi_{2x} \uplus \psi_{3xy}}
+		\end{array}}} 
+\end{multline*}
+that can be re-written:
+\begin{multline*}
+\everymath{\displaystyle}
+\forall v\in \mpar{\fvars{\alpha_{2x}}  \cup \bigcup_{j \in J'} \!\fvars{\beta_{2jx}}} \setminus \mpar{V_2 \uplus V_3 \uplus \fvars{t_{2x}}},\\ \mpar{R_{23}\mpar{s_2, s_{3}} \wedge g_{2x} \implies \operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			 \alpha_{2x}=\alpha_{3xy} \wedge \bigwedge_\subbox{j \in J'_{3xy} \cap H'} \beta_{2jx}=\beta_{3jxy} \\
+			\nwedge g_{3xy} \wedge R_{23}\mpar{s'_{2x}, s'_{3xy}}\psubst{\psi_{2x} \uplus \psi_{3xy}}
+		\end{array}}} 
+\end{multline*}
+
+\item For the third condition. First from the relation between $A_1$ and $A_2$ we have:
+\begin{multline*}
+\forall \mpar{s_1, s_2} \in S_1 \times S_2,\\ V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
+\end{multline*}
+Second, from the relation between $A_2$ and $A_3$ we have:
+\begin{multline*}
+\forall \mpar{s_2, s_3} \in S_2 \times S_3,\\ V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash \left(R_{23}\mpar{s_2, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \right)
+\end{multline*}
+We get:
+
+\newpage
+
+\end{enumerate}
 

### 2021-12-02 2021-Refinement/paper/refinementarticle.tex
notations in proof

@@
 \proof 
-Suppose we have $R_{12}$ a relation between states
-of $A_1$ and of $A_2$;  Suppose we also have $R_{23}$ a relation between states of $A_2$ and of $A_3$. We build a relation between
+If $\wrel{A_1}{A_2}{H}$ then there is $R_{12}$ a relation between states
+of $A_1$ and of $A_2$;  If $\wrel{A_2}{A_3}{H'}$ then there is $R_{23}$ a relation between states of $A_2$ and of $A_3$. We build a relation between
  states of $A_1$ and of $A_3$ as follows:  for each pair of states $s_1$, $s_3$, for each state $s_2$ such that $R_{12}$ relates $s_1$ and $s_2$, and $R_{23}$ relates $s_2$ and $s_3$.
@@
 
-We will show that ($R_{13}$, $H\cap H'$) is a hole-tracking simulation of $A_1$ by  $A_3$.
+We will show that $\wrel{A_1}{A_3}{H\cap H'}$ by exhibiting  $R_{13}$ as a hole-tracking simulation of $A_1$ by  $A_3$.
 

### 2021-12-02 2021-Refinement/paper/refinementarticle.tex
proof

@@
 Let $R_{13}$ be the relation:\\
-  $R_{13}=\{(s_1,s_3) \in S_1\times S_2 | (s_1,s_2) \in R_{12}\wedge (s_2,s_3) \in R_{23} \} $
+  \[R_{13}(s_1,s_3)=\bigvee_{s_2\in S_2}\mpar{R_{12}(s_1,s_2) \land R_{23}(s_2,s_3) } \]
 
@@
 We have:
-\begin{multline*}
+\begin{align*}
 \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar
-{\sigma_{02} \uplus \sigma_{03} \vdash R_{23}\mpar{s_{02}, s_{03}}}\implies\\
-R_{12}\mpar{s_{01},s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02}} \wedge R_{23}\mpar{s_{02}, s_{03}}\psubst{\sigma_{02} \uplus \sigma_{03}}\implies\\
-R_{12}\mpar{s_{01},s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} \wedge R_{23}\mpar{s_{02}, s_{03}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}}\implies\\ \underbrace{R_{12}\mpar{s_{01},s_{02}}\wedge R_{23}\mpar{s_{02}, s_{03}}}_{R_{13} \mpar{s_{01}, s_{03}}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} \implies\\
-\sigma_{01} \uplus \sigma_{03} \vdash R_{13} \mpar{s_{01}, s_{03}}
-\end{multline*}
+{\sigma_{02} \uplus \sigma_{03} \vdash R_{23}\mpar{s_{02}, s_{03}}}&\implies\\
+R_{12}\mpar{s_{01},s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02}} \wedge R_{23}\mpar{s_{02}, s_{03}}\psubst{\sigma_{02} \uplus \sigma_{03}}&\implies\\
+R_{12}\mpar{s_{01},s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} \wedge R_{23}\mpar{s_{02}, s_{03}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}}&\implies\\ 
+\underbrace{R_{12}\mpar{s_{01},s_{02}}\wedge R_{23}\mpar{s_{02}, s_{03}}}_{R_{13} \mpar{s_{01}, s_{03}}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} &\implies\\
+\sigma_{01} \uplus \sigma_{03} \vdash R_{13} &\mpar{s_{01}, s_{03}}
+\end{align*}
 
-\item Consider $\mpar{s_{1}, s_{3}} \in R_{13}$ then there is a set of states of $A_2$ relating  $s_{1}$ and $s_{3}$, let $(t_x)^{x\in X}$ be the family of transition originating from  these states:
-\[R_{13}=\bigcup_{\begin{array}{c}       		
-       			\mpar{s_1,s_{2x}} \in R_{12}\\
-\mpar{s_{2x},s_3}\in R_{23}
-       		\end{array}
-}R_{12}\mpar{s_1,s_{2x}} \wedge R_{23}\mpar{s_{2x},s_3} \]
+\item Consider $\mpar{s_{1}, s_{3}} \in R_{13}$ then there is a set of states $(s_{2p})^{p\in P}$ of $A_2$ relating  $s_{1}$ and $s_{3}$:
+\[R_{13}(s_1,s_3)=\bigcup_{{p\in P}
+}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}} \]
+
+Consider one $s_{2p} \in (s_{2p})^{p\in P}$.
 
@@
 \end{align*}
-there exist an indexed family of OTs originating from $s_2$: 
+there exist an indexed family of OTs originating from $s_{2p}$: 
 \begin{align*}
-\mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X} \subseteq T_2
+\mpar{\OTx{2p}{x}{2px}{2px} \in \fOT{s_{2p}}}^{x \in X_p} 
 \end{align*}
-such that $\forall x \in X, J'_{2x} \cap H = J'_1 \cap H$ and
+such that $\forall x \in X, J'_{2px} \cap H = J'_1 \cap H$ and
 \begin{multline*}
 %\everymath{\displaystyle}
-V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\ \mpar{R_{12}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\ \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X_p} \mpar{\everymath{\displaystyle}
 \begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \\
-			\nwedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \\
+			\nwedge g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}}
 		\end{array}}} 
@@
 %\everymath{\displaystyle}
-\forall v \in \mpar{\fvars{\alpha_{2x}}  \cup \bigcup_{j \in J'} \!\fvars{\beta_{2jx}}} \setminus \mpar{V_1 \uplus V_2 \uplus \fvars{t_1}}, \\ \mpar{R_{12}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\forall v \in \mpar{\fvars{\alpha_{2px}}  \cup \bigcup_{j \in J'} \!\fvars{\beta_{2pxj}}} \setminus \mpar{V_1 \uplus V_2 \uplus \fvars{t_1}}, \\ \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X_p} \mpar{\everymath{\displaystyle}
 \begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2jx} \\
-			\nwedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pjx} \\
+			\nwedge g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}}
 		\end{array}}} \\
@@
 \medskip
-Multiplying the two terms of the implication by $R_{23}\mpar{s_2,s_3}$ we get:
+Adding to the two terms of the implication the predicate $R_{23}\mpar{s_{2p},s_3}$ we get:
 
 \begin{multline*}
- \mpar{R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2,s_3} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+ \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
 \begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2jx} \nwedge\\
-			R_{23}\mpar{s_2,s_3}\wedge g_{2x} \wedge R_{12}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pjx} \\
+			\nwedge g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}} \land R_{23}\mpar{s_{2p},s_3}
 		\end{array}}} \\

### 2021-12-03 2021-Refinement/paper/refinementarticle.tex
proof corrections
proof progess

@@
 
-Consider each condition of the definition of a refinement of open automata.
+We have to prove that the relation $R_{13}$ satisfies the three conditions of the definition of a refinement of open automata.
 \begin{enumerate}
-\item One has to prove it first initial configurations.
+\item $R_{13}$ satisfies initial configurations.
 By knowing that substitutions only have an effect on the variables of the open automaton they belong to, they also produce terms containing only variables of the open automaton they belong to.
@@
 R_{12}\mpar{s_{01},s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} \wedge R_{23}\mpar{s_{02}, s_{03}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}}&\implies\\ 
-\underbrace{R_{12}\mpar{s_{01},s_{02}}\wedge R_{23}\mpar{s_{02}, s_{03}}}_{R_{13} \mpar{s_{01}, s_{03}}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} &\implies\\
-\sigma_{01} \uplus \sigma_{03} \vdash R_{13} &\mpar{s_{01}, s_{03}}
+\underbrace{R_{12}\mpar{s_{01},s_{02}}\wedge R_{23}\mpar{s_{02}, s_{03}}}_{R_{13} \mpar{s_{01}, s_{03}}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} %&\implies\\
  \end{align*}
-
+Hence we get:
+\[\sigma_{01} \uplus \sigma_{03} \vdash R_{13} \mpar{s_{01}, s_{03}}\]
 \item Consider $\mpar{s_{1}, s_{3}} \in R_{13}$ then there is a set of states $(s_{2p})^{p\in P}$ of $A_2$ relating  $s_{1}$ and $s_{3}$:
-\[R_{13}(s_1,s_3)=\bigcup_{{p\in P}
+\[R_{13}(s_1,s_3)=\bigvee_{{p\in P}
 }\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}} \]
 
-Consider one $s_{2p} \in (s_{2p})^{p\in P}$.
+Let's consider any $s_{2p} \in (s_{2p})^{p\in P}$.
 
@@
 %\everymath{\displaystyle}
-\forall v \in \mpar{\fvars{\alpha_{2px}}  \cup \bigcup_{j \in J'} \!\fvars{\beta_{2pxj}}} \setminus \mpar{V_1 \uplus V_2 \uplus \fvars{t_1}}, \\ \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X_p} \mpar{\everymath{\displaystyle}
+\forall v \in \mpar{\fvars{\alpha_{2px}}  \cup \bigcup_{j \in J'_{2px}} \!\fvars{\beta_{2pxj}}} \setminus \mpar{V_1 \uplus V_2 \uplus \fvars{t_1}}, \\ \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X_p} \mpar{\everymath{\displaystyle}
 \begin{array}{l}
-			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pjx} \\
+			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \\
 			\nwedge g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}}
@@
 Adding to the two terms of the implication the predicate $R_{23}\mpar{s_{2p},s_3}$ we get:
+\begin{align*}
+R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies\hspace{5.5cm}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \land\\
+			 g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}} \land R_{23}\mpar{s_{2p},s_3}
+		\end{array}} \\
+\end{align*}
 
-\begin{multline*}
- \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pjx} \\
-			\nwedge g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}} \land R_{23}\mpar{s_{2p},s_3}
-		\end{array}}} \\
-	\end{multline*}
-
-On the other side, from the relation between $A_2$ and $A_3$ we have for any open transition $t_{2x}$ in $T_2$ originating from $s_2$:
+On the other side, according the relation between $A_2$ and $A_3$ we have for any open transition $t_{2px}$ in $T_2$ originating from $s_{2p}$:
 \begin{align*}
-\OTx{2}{x}{2x}{2x} \in \fOT{s_2}
+\OTx{2p}{x}{2px}{2px} \in \fOT{s_{2p}}
 \end{align*}
@@
 \begin{align*}
-\mpar{\OTx{3}{xy}{3xy}{3xy} \in \fOT{s_3}}^{y \in Y} \subseteq T_3
+\mpar{\OTx{3}{pxy}{3pxy}{3pxy} \in \fOT{s_3}}^{y \in Y} 
 \end{align*}
-such that $\forall y \in Y, J'_{2x} \cap H' = J'_{3xy} \cap H'$ and
+such that $\forall y \in Y, J'_{2px} \cap H' = J'_{3pxy} \cap H'$ and
 \begin{multline*}
 \everymath{\displaystyle}
-V_2 \uplus V_3 \uplus \fvars{t_{2x}} \vdash\\\hspace{2em} \mpar{R_{23}\mpar{s_2, s_{3}} \wedge g_{2x} \implies \operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
+V_2 \uplus V_3 \uplus \fvars{t_{2px}} \vdash\\\hspace{2em} \mpar{R_{23}\mpar{s_{2p}, s_{3}} \wedge g_{2px} \implies \operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
 \begin{array}{l}
-			 \alpha_{2x}=\alpha_{3xy} \wedge \bigwedge_\subbox{j \in J'_{3xy} \cap H'} \beta_{2jx}=\beta_{3jxy} \\
-			\nwedge g_{3xy} \wedge R_{23}\mpar{s'_{2x}, s'_{3xy}}\psubst{\psi_{2x} \uplus \psi_{3xy}}
+			 \alpha_{2px}=\alpha_{3pxy} \wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{2pxj}=\beta_{3pxyj} \\
+			\nwedge g_{3pxy} \wedge R_{23}\mpar{s'_{2px}, s'_{3xy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
 		\end{array}}} 
@@
 \everymath{\displaystyle}
-\forall v\in \mpar{\fvars{\alpha_{2x}}  \cup \bigcup_{j \in J'} \!\fvars{\beta_{2jx}}} \setminus \mpar{V_2 \uplus V_3 \uplus \fvars{t_{2x}}},\\ \mpar{R_{23}\mpar{s_2, s_{3}} \wedge g_{2x} \implies \operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
+\forall v\in \mpar{\fvars{\alpha_{2px}}  \cup \bigcup_{j \in J'_{3pxy}} \!\fvars{\beta_{2jpx}}} \setminus \mpar{V_2 \uplus V_3 \uplus \fvars{t_{2px}}},\\ \mpar{R_{23}\mpar{s_{2p}, s_{3}} \wedge g_{2px} \implies \operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
 \begin{array}{l}
-			 \alpha_{2x}=\alpha_{3xy} \wedge \bigwedge_\subbox{j \in J'_{3xy} \cap H'} \beta_{2jx}=\beta_{3jxy} \\
-			\nwedge g_{3xy} \wedge R_{23}\mpar{s'_{2x}, s'_{3xy}}\psubst{\psi_{2x} \uplus \psi_{3xy}}
+			 \alpha_{2px}=\alpha_{3pxy} \wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{2pxj}=\beta_{3pxyj} \\
+			\nwedge g_{3pxy} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
 		\end{array}}} 
 \end{multline*}
+The following  can be derived from both cases:
+$\forall x \in X, J'_{2px} \cap H = J'_1 \cap H$
+$\forall y \in Y, J'_{2px} \cap H' = J'_{3pxy} \cap H'$ and 
+implies
+$\forall x \in X \forall y \in Y,  J'_1 \cap (H \cap H') = J'_{3pxy} \cap (H\cap H')$
+In addition, we have
 
-\item For the third condition. First from the relation between $A_1$ and $A_2$ we have:
+\begin{align*}
+\forall v \in \mpar{\fvars{\alpha_{2px}}  \cup \bigcup_{j \in J'_{2px}} \!\fvars{\beta_{2pxj}}} \setminus \mpar{V_1 \uplus V_2 \uplus \fvars{t_1}},
+\forall v\in \mpar{\fvars{\alpha_{2px}}  \cup \bigcup_{j \in J'_{3pxy}} \!\fvars{\beta_{2jpx}}} \setminus \mpar{V_2 \uplus V_3 \uplus \fvars{t_{2px}}},\\
+R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies \hspace{4.5cm}\\\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj}  \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}} \\
+		\operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			 \alpha_{2px}=\alpha_{3pxy} \wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{2pxj}=\beta_{3pxyj} \\
+			\nwedge g_{3pxy} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
+		\end{array}}	
+		\end{array}} \\
+\end{align*}
+
+After simplification, we get:
+\begin{align*}
+R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies 
+\hspace{5.5cm}\\
+\operatorname*{\bigsymb{\bigvee}}_{x \in X} 
+\operatorname*{\bigsymb{\bigvee}}_{y \in Y}
+\mpar{\everymath{\displaystyle}
+\begin{array}{l}
+\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap (H\cap H')} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
+R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
+\end{array}}
+\end{align*}
+
+Because of the domain of the substitutions of the relations, we have:
+\begin{align*}
+\underbrace{R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}_{R_{13}\mpar{s_1, s_3}} \wedge g_1 \implies 
+\hspace{5.5cm}\\
+\operatorname*{\bigsymb{\bigvee}}_{x \in X} 
+\operatorname*{\bigsymb{\bigvee}}_{y \in Y}
+\mpar{\everymath{\displaystyle}
+\begin{array}{l}
+\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
+\underbrace{R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}}_{R_{12}\mpar{s'_1,s'_{3pxy}}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}
+\end{array}}
+\end{align*}	
+This allows us to conclude, with $R_{13}(s_1,s_3)=\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}$: 
+\begin{align*}
+R_{13}\mpar{s_1, s_3} \wedge g_1 \implies 
+\hspace{7.5cm}\\
+\operatorname*{\bigsymb{\bigvee}}_{p \in P}
+\operatorname*{\bigsymb{\bigvee}}_{x \in X} 
+\operatorname*{\bigsymb{\bigvee}}_{y \in Y}
+\mpar{\everymath{\displaystyle}
+\begin{array}{l}
+\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{1j}=\beta_{3jpxy} \\\wedge g_{3pxy}\wedge \\
+{R_{12}\mpar{s'_1,s'_{3pxy}}}\psubst{\psi_1  \uplus \psi_{3pxy}}
+\end{array}}
+\end{align*}	
+This provides the desired conclusion:
+\begin{align*}
+\mpar{R_{13}\mpar{s_1, s_3} \wedge g_1 \implies 
+\operatorname*{\bigsymb{\bigvee}}_{z \in Z}
+\mpar{\everymath{\displaystyle}
+\begin{array}{l}
+\alpha_1=\alpha_{3z}\wedge \bigwedge_\subbox{j \in J'_{3z} \cap H'} \beta_{1j}=\beta_{3jz}\\ \wedge g_{3z}\wedge 
+{R_{12}\mpar{s'_1,s'_{3z}}}\psubst{\psi_1  \uplus \psi_{3z}}
+\end{array}}}
+\end{align*}	
+\item Concerning the condition on the deadlock reducing. According to the relation between   $A_2$ and $A_3$ we have forall $\mpar{s_{2p}, s_3} \in S_2 \times S_3$:
 \begin{multline*}
-\forall \mpar{s_1, s_2} \in S_1 \times S_2,\\ V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R_{12}\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
+ V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash \left(R_{23}\mpar{s_{2p}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} \right)
 \end{multline*}
-Second, from the relation between $A_2$ and $A_3$ we have:
+that can be rewritten:
+\begin{align*}
+R_{23}\mpar{s_{2p}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} 
+\end{align*}
+By adding the term $R_{12}\mpar{s_1,s_{2p}}$ to both sides of the implication, we get:
+\begin{align*}
+R_{12}\mpar{s_1,s_{2p}}\wedge R_{23}\mpar{s_{2p}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies R_{12}\mpar{s_1,s_{2p}}\wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}}
+\end{align*}
+Yet according to the relation between $A_1$ and $A_2$ we have  forall $\mpar{s_1, s_{2p}} \in S_1 \times S_2$:
 \begin{multline*}
-\forall \mpar{s_2, s_3} \in S_2 \times S_3,\\ V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash \left(R_{23}\mpar{s_2, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \right)
+ V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{2p} \in \fOT{s_{2p}}} \fvars{t_{2p}} \vdash \left(R_{12}\mpar{s_1, s_{2p}} \wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
 \end{multline*}
-We get:
+Then,
+\begin{align*}
+R_{12}\mpar{s_1, s_{2p}} \wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
+\end{align*}
+The desired result will be obtained by transitivity of
 

### 2021-12-03 2021-Refinement/paper/refinementarticle.tex
proof

@@
 %\everymath{\displaystyle}
-\forall v \in \mpar{\fvars{\alpha_{2px}}  \cup \bigcup_{j \in J'_{2px}} \!\fvars{\beta_{2pxj}}} \setminus \mpar{V_1 \uplus V_2 \uplus \fvars{t_1}}, \\ \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X_p} \mpar{\everymath{\displaystyle}
+\forall v \in \mpar{\fvars{\alpha_{1}}  \cup \bigcup_{j \in J'_{2px} \cap H} \!\fvars{\beta_{1j}}} \setminus \mpar{V_1 \uplus V_2 \uplus \fvars{t_1}}, \\ \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X_p} \mpar{\everymath{\displaystyle}
 \begin{array}{l}
@@
 \everymath{\displaystyle}
-\forall v\in \mpar{\fvars{\alpha_{2px}}  \cup \bigcup_{j \in J'_{3pxy}} \!\fvars{\beta_{2jpx}}} \setminus \mpar{V_2 \uplus V_3 \uplus \fvars{t_{2px}}},\\ \mpar{R_{23}\mpar{s_{2p}, s_{3}} \wedge g_{2px} \implies \operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
+\forall v\in \mpar{\fvars{\alpha_{2px}}  \cup \bigcup_{j \in J'_{3pxy}
+\cap H'} \!\!\fvars{\beta_{2pxj}}} \setminus \mpar{V_2 \uplus V_3 \uplus \fvars{t_{2px}}},\\ \mpar{R_{23}\mpar{s_{2p}, s_{3}} \wedge g_{2px} \implies \operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
 \begin{array}{l}
@@
 \end{multline*}
-The following  can be derived from both cases:
-$\forall x \in X, J'_{2px} \cap H = J'_1 \cap H$
-$\forall y \in Y, J'_{2px} \cap H' = J'_{3pxy} \cap H'$ and 
-implies
-$\forall x \in X \forall y \in Y,  J'_1 \cap (H \cap H') = J'_{3pxy} \cap (H\cap H')$
-In addition, we have
-
+The following  can be derived from the two previous cases: \\
+$\forall x \in X, J'_{2px} \cap H = J'_1 \cap H$ and
+$\forall y \in Y, J'_{2px} \cap H' = J'_{3pxy} \cap H'$ leading to the conclusion\\
+$\forall x \in X, \forall y \in Y,  J'_1 \cap (H \cap H') = J'_{3pxy} \cap (H\cap H')$ \\
+In addition, we get: \\
+$\displaystyle {\forall v \in \mpar{\fvars{\alpha_{1}}  \cup \bigcup_{j \in J'_{2px} \cap H} \!\fvars{\beta_{1j}}  \cup \fvars{\alpha_{2px}}  \cup \bigcup_{j \in J'_{3pxy} \cap H'} \!\fvars{\beta_{2pxj}}} } \setminus \\ \mpar{V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1}\uplus \fvars{t_{2px}}}
+$
 \begin{align*}
-\forall v \in \mpar{\fvars{\alpha_{2px}}  \cup \bigcup_{j \in J'_{2px}} \!\fvars{\beta_{2pxj}}} \setminus \mpar{V_1 \uplus V_2 \uplus \fvars{t_1}},
-\forall v\in \mpar{\fvars{\alpha_{2px}}  \cup \bigcup_{j \in J'_{3pxy}} \!\fvars{\beta_{2jpx}}} \setminus \mpar{V_2 \uplus V_3 \uplus \fvars{t_{2px}}},\\
 R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies \hspace{4.5cm}\\\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
@@
 		\end{array}}	
-		\end{array}} \\
+		\end{array}} 
 \end{align*}		
-
-After simplification, we get:
+With the restriction of the domain and the simplification of the formula, we get:\\
+$\displaystyle {\forall v \in \mpar{\fvars{\alpha_{1}}  \cup\!\!\!
+\bigcup_{j \in J'_{3pxy} \cap H \cap H'} \!\!\!\fvars{\beta_{1j}}  \cup \fvars{\alpha_{2px}}  \cup\!\!\!
+\bigcup_{j \in J'_{3pxy} \cap H\cap H'} \!\!\!\fvars{\beta_{2pxj}}} } \setminus \\ \mpar{V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1}\uplus \fvars{t_{2px}}}
+$
 \begin{align*}
@@
 \end{align*}	
-This allows us to conclude, with $R_{13}(s_1,s_3)=\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}$: 
+This allows us to conclude, with ${\displaystyle R_{13}(s_1,s_3)=\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}}$:
+
+$\forall p \in P, \forall x \in X, \forall y \in Y,  J'_1 \cap (H \cap H') = J'_{3pxy} \cap (H\cap H'),$\\
+$\displaystyle {\forall v \in \mpar{\fvars{\alpha_{1}}  \cup\!\!\! \bigcup_{j \in J'_{3pxy} \cap H \cap H'} \!\!\!\fvars{\beta_{1j} } } \setminus  \mpar{V_1 \uplus  V_3 \uplus \fvars{t_1}}}, $
 \begin{align*}
@@
 \end{align*}	
-This provides the desired conclusion:
+This provides the desired conclusion:\\
+$\forall z \in Z,  J'_1 \cap (H \cap H') = J'_{3z} \cap (H\cap H')$\\
+$\displaystyle {\forall v \in \mpar{\fvars{\alpha_{1}}  \cup\!\!\! \bigcup_{j \in J'_{3z} \cap H \cap H'} \!\!\!\fvars{\beta_{1j} } } \setminus  \mpar{V_1 \uplus  V_3 \uplus \fvars{t_1}}} ,  $
 \begin{align*}
@@
 \end{align*}	
-\item Concerning the condition on the deadlock reducing. According to the relation between   $A_2$ and $A_3$ we have forall $\mpar{s_{2p}, s_3} \in S_2 \times S_3$:
+\item Concerning the condition of deadlock reducing. According to the relation between   $A_2$ and $A_3$ we have forall $\mpar{s_{2p}, s_3} \in S_2 \times S_3$:
 \begin{multline*}

### 2021-12-03 2021-Refinement/paper/refinementarticle.tex
transistivity proof 1) and 2)

@@
 R_{12}\mpar{s_{01},s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} \wedge R_{23}\mpar{s_{02}, s_{03}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}}&\implies\\ 
-\underbrace{R_{12}\mpar{s_{01},s_{02}}\wedge R_{23}\mpar{s_{02}, s_{03}}}_{R_{13} \mpar{s_{01}, s_{03}}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} %&\implies\\
+\underbrace{R_{12}\mpar{s_{01},s_{02}}\wedge R_{23}\mpar{s_{02}, s_{03}}}_{\implies R_{13} \mpar{s_{01}, s_{03}}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} %&\implies\\
  \end{align*}
@@
 \medskip
-Adding to the two terms of the implication the predicate $R_{23}\mpar{s_{2p},s_3}$ we get:
+Adding to both sides of the implication the predicate $R_{23}\mpar{s_{2p},s_3}$ we get:
 \begin{align*}
@@
 			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj}  \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}} \\ 
+\land
 		\operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
@@
 \begin{align*}
-\underbrace{R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}_{R_{13}\mpar{s_1, s_3}} \wedge g_1 \implies 
+R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies 
 \hspace{5.5cm}\\
@@
 \alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
-\underbrace{R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}}_{R_{12}\mpar{s'_1,s'_{3pxy}}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}
+R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}
 \end{array}}
 \end{align*}
-This allows us to conclude, with ${\displaystyle R_{13}(s_1,s_3)=\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}}$:
 
-$\forall p \in P, \forall x \in X, \forall y \in Y,  J'_1 \cap (H \cap H') = J'_{3pxy} \cap (H\cap H'),$\\
-$\displaystyle {\forall v \in \mpar{\fvars{\alpha_{1}}  \cup\!\!\! \bigcup_{j \in J'_{3pxy} \cap H \cap H'} \!\!\!\fvars{\beta_{1j} } } \setminus  \mpar{V_1 \uplus  V_3 \uplus \fvars{t_1}}}, $
-\begin{align*}
-R_{13}\mpar{s_1, s_3} \wedge g_1 \implies 
-\hspace{7.5cm}\\
-\operatorname*{\bigsymb{\bigvee}}_{p \in P}
+This is valid for all $s_{2p} \in (s_{2p})^{p\in P}$.
+We need to rely on the disjunction of all possible paths to relate $s_1$ and $s_3$ with ${\displaystyle R_{13}(s_1,s_3)=\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}}$.
+
+\begin{multline*}
+\operatorname*{\bigsymb{\bigvee}}_{p\in P} \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1} \implies 
+\hspace{5.5cm}\\
+\operatorname*{\bigsymb{\bigvee}}_{p\in P}
 \operatorname*{\bigsymb{\bigvee}}_{x \in X} 
@@
 \begin{array}{l}
-\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{1j}=\beta_{3jpxy} \\\wedge g_{3pxy}\wedge \\
-{R_{12}\mpar{s'_1,s'_{3pxy}}}\psubst{\psi_1  \uplus \psi_{3pxy}}
+\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
+\underbrace{R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}}_{\implies R_{13}\mpar{s'_1,s'_{3pxy}}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}
 \end{array}}
-\end{align*}	
+\end{multline*}
+
+This allows us to conclude that the family of open transitions of $A_3$ indexed over $p$, $x$,  and $y$ simulates the original open transition \TODO{re-write the set of OTs or not?} with (note that $\psi_{2px}$ has no effect on variables of $A1$ and $A3$:
+\begin{multline*}
+R_{13}(s_1,s_3)  \wedge g_1 \implies 
+\hspace{5.5cm}\\
+\operatorname*{\bigsymb{\bigvee}}_{p\in P}
+\operatorname*{\bigsymb{\bigvee}}_{x \in X} 
+\operatorname*{\bigsymb{\bigvee}}_{y \in Y}
+\mpar{\everymath{\displaystyle}
+\begin{array}{l}
+\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
+{\implies R_{13}\mpar{s'_1,s'_{3pxy}}}\psubst{\psi_1  \uplus \psi_{3pxy}}
+\end{array}}
+\end{multline*}
+
+\TODO{[LUDO] je suis un peu embete par le fait qu on se soit debarrasse des quantifiers et qu ils reviennent miraculeusement ici, a completer ou au moins commeter a mon avis (1footnote peut suffire si on est bien convaincus)}
 This provides the desired conclusion:\\

### 2021-12-06 2021-Refinement/paper/refinementarticle.tex
correction proof

@@
  \end{align*}
-Hence we get:
+Since $\sigma_{02}$ has no effect on variables of $s_{01}$ and $s_{03}$ thus we get:
 \[\sigma_{01} \uplus \sigma_{03} \vdash R_{13} \mpar{s_{01}, s_{03}}\]
@@
 $\displaystyle {\forall v \in \mpar{\fvars{\alpha_{1}}  \cup\!\!\!
-\bigcup_{j \in J'_{3pxy} \cap H \cap H'} \!\!\!\fvars{\beta_{1j}}  \cup \fvars{\alpha_{2px}}  \cup\!\!\!
-\bigcup_{j \in J'_{3pxy} \cap H\cap H'} \!\!\!\fvars{\beta_{2pxj}}} } \setminus \\ \mpar{V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1}\uplus \fvars{t_{2px}}}
+\!\!\bigcup_{j \in J'_{3pxy} \cap H \cap H'} \!\!\!\!\!\fvars{\beta_{1j}}  \cup \fvars{\alpha_{2px}}  \cup\!\!\!
+\!\!\bigcup_{j \in J'_{3pxy} \cap H\cap H'} \!\!\!\!\!\fvars{\beta_{2pxj}}} } \setminus \\ \mpar{V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1}\uplus \fvars{t_{2px}}}
 $
@@
 \begin{array}{l}
-\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
+\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap (H\cap H')} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
 R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}
@@
 \begin{array}{l}
-\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
+\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap (H\cap H')} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
 \underbrace{R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}}_{\implies R_{13}\mpar{s'_1,s'_{3pxy}}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}
@@
 \end{multline*}
-
-This allows us to conclude that the family of open transitions of $A_3$ indexed over $p$, $x$,  and $y$ simulates the original open transition \TODO{re-write the set of OTs or not?} with (note that $\psi_{2px}$ has no effect on variables of $A1$ and $A3$:
+We have:
+\begin{multline*}
+R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}} \implies\\ R_{13}\mpar{s'_1,s'_{3pxy}}
+\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}
+\end{multline*}
+Since $\psi_{2px}$ has no effect on variables of $A1$ and $A3$, it then implies:
+\begin{align*}
+R_{13}\mpar{s'_1,s'_{3pxy}}\psubst{\psi_1  \uplus \psi_{3pxy}}
+\end{align*}
+This allows us to conclude that the family of open transitions of $A_3$ indexed over $p$, $x$,  and $y$ simulates the original open transition \TODO{re-write the set of OTs or not?} with note that $\psi_{2px}$ has no effect on variables of $A1$ and $A3$:
 \begin{multline*}
@@
 \begin{array}{l}
-\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
-{\implies R_{13}\mpar{s'_1,s'_{3pxy}}}\psubst{\psi_1  \uplus \psi_{3pxy}}
+\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap (H\cap H')} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy} \\
+{\wedge R_{13}\mpar{s'_1,s'_{3pxy}}}\psubst{\psi_1  \uplus \psi_{3pxy}}
 \end{array}}
 \end{multline*}
-
+Overall, we have a family of open transitions $t^{p\in P,x\in X,y\in Y}_{pxy} \subseteq T_3$ that should simulate $t_1$.
+All  combinations of elements in $P$, $X$, and $Y$ provide a set $Z$ of weak open transitions.
+This allows us to get the desired conclusion, that there is a set of weak open transitions indexed over $Z$:\\
 \TODO{[LUDO] je suis un peu embete par le fait qu on se soit debarrasse des quantifiers et qu ils reviennent miraculeusement ici, a completer ou au moins commeter a mon avis (1footnote peut suffire si on est bien convaincus)}
-This provides the desired conclusion:\\
+%This provides the desired conclusion:\\
 $\forall z \in Z,  J'_1 \cap (H \cap H') = J'_{3z} \cap (H\cap H')$\\
@@
 \begin{array}{l}
-\alpha_1=\alpha_{3z}\wedge \bigwedge_\subbox{j \in J'_{3z} \cap H'} \beta_{1j}=\beta_{3jz}\\ \wedge g_{3z}\wedge 
+\alpha_1=\alpha_{3z}\wedge \bigwedge_\subbox{j \in J'_{3z} \cap (H\cap H')} \beta_{1j}=\beta_{3jz}\\ \wedge g_{3z}\wedge 
 {R_{12}\mpar{s'_1,s'_{3z}}}\psubst{\psi_1  \uplus \psi_{3z}}
@@
 \end{align*}	
+\medskip
 \item Concerning the condition of deadlock reducing. According to the relation between   $A_2$ and $A_3$ we have forall $\mpar{s_{2p}, s_3} \in S_2 \times S_3$:

### 2021-12-08 2021-Refinement/paper/refinementarticle.tex
correction proof
proof suite

@@
 \begin{array}{l}
-			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \\
-			\nwedge g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}}
+			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \nwedge\\
+			 g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}}
 		\end{array}}} 
@@
 \begin{array}{l}
-			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \\
-			\nwedge g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}}
+			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \nwedge\\
+			 g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}}
 		\end{array}}} \\
@@
 \begin{array}{l}
-			 \alpha_{2px}=\alpha_{3pxy} \wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{2pxj}=\beta_{3pxyj} \\
-			\nwedge g_{3pxy} \wedge R_{23}\mpar{s'_{2px}, s'_{3xy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
+			 \alpha_{2px}=\alpha_{3pxy} \wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{2pxj}=\beta_{3pxyj} \nwedge \\
+			g_{3pxy} \wedge R_{23}\mpar{s'_{2px}, s'_{3xy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
 		\end{array}}} 
@@
 \begin{array}{l}
-			 \alpha_{2px}=\alpha_{3pxy} \wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{2pxj}=\beta_{3pxyj} \\
-			\nwedge g_{3pxy} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
+			 \alpha_{2px}=\alpha_{3pxy} \wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{2pxj}=\beta_{3pxyj} \nwedge\\
+			 g_{3pxy} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
 		\end{array}}} 
@@
 $\forall x \in X, J'_{2px} \cap H = J'_1 \cap H$ and
-$\forall y \in Y, J'_{2px} \cap H' = J'_{3pxy} \cap H'$ leading to the conclusion\\
+$\forall y \in Y, J'_{2px} \cap H' = J'_{3pxy} \cap H'$ leading to the conclusion:\\
 $\forall x \in X, \forall y \in Y,  J'_1 \cap (H \cap H') = J'_{3pxy} \cap (H\cap H')$ \\
@@
 \begin{array}{l}
-			 \alpha_{2px}=\alpha_{3pxy} \wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{2pxj}=\beta_{3pxyj} \\
-			\nwedge g_{3pxy} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
+			 \alpha_{2px}=\alpha_{3pxy} \wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{2pxj}=\beta_{3pxyj} \nwedge\\
+			 g_{3pxy} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
 		\end{array}}	
@@
 \begin{multline*}
-R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}} \implies\\ R_{13}\mpar{s'_1,s'_{3pxy}}
+R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}} \implies\\ R_{13}\mpar{s'_1,s'_{3pxy}}
 \psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}
@@
 \begin{array}{l}
-\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap (H\cap H')} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy} \\
+\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap (H\cap H')} \beta_{1j}=\beta_{3jpxy} \wedge\\ g_{3pxy} 
 {\wedge R_{13}\mpar{s'_1,s'_{3pxy}}}\psubst{\psi_1  \uplus \psi_{3pxy}}
@@
 \begin{array}{l}
-\alpha_1=\alpha_{3z}\wedge \bigwedge_\subbox{j \in J'_{3z} \cap (H\cap H')} \beta_{1j}=\beta_{3jz}\\ \wedge g_{3z}\wedge 
+\alpha_1=\alpha_{3z}\wedge \bigwedge_\subbox{j \in J'_{3z} \cap (H\cap H')} \beta_{1j}=\beta_{3jz} \wedge \\g_{3z}\wedge 
 {R_{12}\mpar{s'_1,s'_{3z}}}\psubst{\psi_1  \uplus \psi_{3z}}
@@
 that can be rewritten:
-\begin{align*}
+\begin{multline*}
+\everymath{\displaystyle}
+\forall v\in \mpar{\fvars{\alpha_{3}}  \cup \!\!\bigcup_{j \in J'_{3}} \!\!\fvars{\beta_{3j}}} \cup \mpar{\fvars{\alpha_{2px}}  \cup \!\!\! \bigcup_{j \in J'_{2p}} \!\!\!\fvars{\beta_{2pxj}}}
+ \setminus \mpar{V_2\! \uplus\!V_3 \uplus\!\! \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3}},\\
 R_{23}\mpar{s_{2p}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} 
-\end{align*}
+\end{multline*}
 By adding the term $R_{12}\mpar{s_1,s_{2p}}$ to both sides of the implication, we get:
@@
 R_{12}\mpar{s_1,s_{2p}}\wedge R_{23}\mpar{s_{2p}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies R_{12}\mpar{s_1,s_{2p}}\wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}}
+\end{align*}
+This is valid for all $s_{2p} \in (s_{2p})^{p\in P}$ then we have:
+\begin{align*}
+\operatorname*{\bigsymb{\bigvee}}_{p\in P}\mpar{
+R_{12}\mpar{s_1,s_{2p}}\wedge R_{23}\mpar{s_{2p}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies R_{12}\mpar{s_1,s_{2p}}\wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}}}
+\end{align*}
+This results in:
+\begin{align*}
+R_{13}\mpar{s_1,s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \operatorname*{\bigsymb{\bigvee}}_{p\in P}\mpar{ R_{12}\mpar{s_1,s_{2p}}\wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}}}
 \end{align*}
@@
 \end{multline*}
-Then,
+This can be rewritten as follows: 
+\begin{multline*}
+\everymath{\displaystyle}
+\forall v\in \mpar{\fvars{\alpha_{2px}}  \cup \!\! \bigcup_{j \in J'_{2p}} \!\! \fvars{\beta_{2pxj}}}\cup \mpar{\fvars{\alpha_{1}}  \cup\!\! \bigcup_{j \in J'_{1}} \!\!\fvars{\beta_{1j}}}
+ \setminus \mpar{V_1\! \uplus\! V_2\!\! \uplus \biguplus_\subbox{t_{2p} \in \fOT{s_{2p}}} \fvars{t_{2p}}},\\
+R_{12}\mpar{s_1, s_{2p}} \wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
+\end{multline*}
+In the same way as this formula is valid for all $s_{2p} \in (s_{2p})^{p\in P}$, we get:
 \begin{align*}
-R_{12}\mpar{s_1, s_{2p}} \wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
+\operatorname*{\bigsymb{\bigvee}}_{p\in P}\mpar{R_{12}\mpar{s_1, s_{2p}} \wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} }  \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
 \end{align*}
-The desired result will be obtained by transitivity of
-
-\newpage
+By using transitive property of implication on formula obtained form both relations and by removing the $A_2$ variables that have not effect on   $A_1$ et  $A_3$, we get:
+\begin{multline*}
+\everymath{\displaystyle}
+\forall v\in \mpar{\fvars{\alpha_{3}}  \cup \!\!\bigcup_{j \in J'_{3}} \!\!\fvars{\beta_{3j}}} \cup \mpar{\fvars{\alpha_{1}}  \cup\!\! \bigcup_{j \in J'_{1}} \!\!\fvars{\beta_{1j}}}
+ \setminus \mpar{V_1\! \uplus\!V_3 \uplus\!\! \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3}},\\
+R_{13}\mpar{s_1,s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3}
+\implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
+\end{multline*}
+This allows us to get the desired result:
+\begin{multline*}
+V_1 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3}
+\vdash R_{13}\mpar{s_1,s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3}
+\implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
+\end{multline*}
 

### 2021-12-09 2021-Refinement/paper/refinementarticle.tex
theorem 2 and proof sketch

@@
 \begin{definition}[Open automata refinement]\label{Def:OA-Refinement}
-For two open automata \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a refinement of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a relation $R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that:
+For two open automata\\ \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a refinement of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a relation $R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that:
 \item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
@@
 \end{lemma}
-The relation  \(\wrel{}{}{H}\) is reflexive,  \(\wrel{A}{A}{H}\),  by taking $R\mpar{s_1, s_2} \mapsto \displaystyle\bigwedge_\subbox{v \in vars(s_1)} {v=v}$ to be $s_1= s_2$  and checking the above conditions (Definition \ref{Def:OA-Refinement}), we can see that\\
+The relation  \(\wrel{}{}{H}\) is reflexive,  \(\wrel{A}{A}{H}\),  by taking $R\mpar{s_1, s_2} \mapsto \displaystyle\bigwedge_\subbox{v \in vars(s_1)} {v=v}$ to be $s_1= s_2$  and checking the above conditions (Definition \ref{Def:OA-Refinement}), we can see that \TODO{finish the sentence}\\
 
 \begin{theorem}[Transitivity]
-If $\wrel{A_1}{A_2}{H}$ and $\wrel{A_2}{A_3}{H}'$, then $\wrel{A_1}{A_3}{H\cap H'}$.
+If $\wrel{A_1}{A_2}{H}$ and $\wrel{A_2}{A_3}{H'}$, then $\wrel{A_1}{A_3}{H\cap H'}$.
 \end{theorem}
-\TODO{proof in appendix + proof sketch}
+
+Appendix~\ref{sec:proof-transitivity} presents the proof.
+It is done classically by identifying the relation between $A_1$ and $A_3$ that is a refinement.
+What is less classical is the definition of this relation because it is a boolean formula.
+For each couple of states  $s_1$ and $s_3$ of $A_1$ and $A_3$ we build a a formula that defines the refinement relation.
+To do this, we take the disjunction of formulas relating $s_1$ and $s_3$, and passing by all states $s_2$ of $A_2$.
+More precisely, we define a relation of the following form:
+  \[R_{13}(s_1,s_3)=\bigvee_{s_2\in S_2}\mpar{R_{12}(s_1,s_2) \land R_{23}(s_2,s_3) } \]
+We then prove that this relation defines is a refinement, according to Definition~\ref{Def:OA-Refinement}.
+
+\TODO{find an informal introduction to the following:}
+The composition of $A_1$ and $A_3$ is a refinement of the composition of $A_2$ and $A_3$ provided $A_1$ is a refinement of $A_2$ and the hole in which we are composing inside $A_1$ and $A_2$ is tracked by the refinement relation.
+
+\begin{theorem}[Context refinement]
+Let $A_1$, $A_2$ and $A_3$ be three open automata with $\wrel{A_1}{A_2}{H}$. 
+Suppose that \(k \in H\) and that \(A_1\subst{A_3}{k}\) is non-locking.
+We have: \[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{J_3 \uplus H \setminus \mbrc{k}}\].
+\end{theorem}
 
@@
 
-\section{a recuperer si on se rend comtpte que c'est utile}
+\section{a recuperer si on se rend compte que c'est utile}
 When we will introduce refinements in Section \ref{sec:prelref}, setting an undefined variable will be considered a valid refinement, for instance a \(5\) bits register is a particular \(n\) bits register.
@@
 \appendix
-\section{Proof of transitivity}
+\section{Proof of Transitivity}\label{sec:proof-transitivity}
 \begin{quote}
@@
 \end{multline*}
-In the same way as this formula is valid for all $s_{2p} \in (s_{2p})^{p\in P}$, we get:
+This formula is valid for all $s_{2p} \in (s_{2p})^{p\in P}$,  thus we can state the following:
 \begin{align*}
@@
 
+\section{Proof of Context Refinement}
+
  \bibliographystyle{splncs04}

### 2021-12-10 2021-Refinement/paper/refinementarticle.tex
debut preuve thm2

@@
 \medskip
-Adding to both sides of the implication the predicate $R_{23}\mpar{s_{2p},s_3}$ we get:
+Adding to both sides of the implication the predicate $R_{23}\mpar{s_{2p},s_3}$ we get: \footnote{Note for the sake of readability, when we justify each step in a a proof
+we omit to rewrite the quantification over of formula which remains unchanged.}
 \begin{align*}
@@
 \end{multline*}
-We have:
+Indeed, we have:
 \begin{multline*}
@@
 \end{align*}
-This allows us to conclude that the family of open transitions of $A_3$ indexed over $p$, $x$,  and $y$ simulates the original open transition \TODO{re-write the set of OTs or not?} with note that $\psi_{2px}$ has no effect on variables of $A1$ and $A3$:
+This allows us to conclude that the family of open transitions of $A_3$ indexed over $p$, $x$,  and $y$ simulates the original open transition  with note that $\psi_{2px}$ has no effect on variables of $A_1$ and $A_3$:
 \begin{multline*}
@@
 This allows us to get the desired conclusion, that there is a set of weak open transitions indexed over $Z$:\\
-\TODO{[LUDO] je suis un peu embete par le fait qu on se soit debarrasse des quantifiers et qu ils reviennent miraculeusement ici, a completer ou au moins commeter a mon avis (1footnote peut suffire si on est bien convaincus)}
 %This provides the desired conclusion:\\
@@
 \medskip
-\item Concerning the condition of deadlock reducing. According to the relation between   $A_2$ and $A_3$ we have forall $\mpar{s_{2p}, s_3} \in S_2 \times S_3$:
+\item Concerning the condition of deadlock reducing. According to the relation between   $A_2$ and $A_3$ we have for all $\mpar{s_{2p}, s_3} \in S_2 \times S_3$:
 \begin{multline*}
@@
 \everymath{\displaystyle}
-\forall v\in \mpar{\fvars{\alpha_{2px}}  \cup \!\! \bigcup_{j \in J'_{2p}} \!\! \fvars{\beta_{2pxj}}}\cup \mpar{\fvars{\alpha_{1}}  \cup\!\! \bigcup_{j \in J'_{1}} \!\!\fvars{\beta_{1j}}}
+\forall v\in \mpar{\fvars{\alpha_{2px}}  \cup \!\! \bigcup_{\begin{array}{c} p\in P\\ j \in J'_{2p}
+\end{array}} \!\! \fvars{\beta_{2pxj}}}\cup \mpar{\fvars{\alpha_{1}}  \cup\!\! \bigcup_{j \in J'_{1}} \!\!\fvars{\beta_{1j}}}
  \setminus \mpar{V_1\! \uplus\! V_2\!\! \uplus \biguplus_\subbox{t_{2p} \in \fOT{s_{2p}}} \fvars{t_{2p}}},\\
@@
 \section{Proof of Context Refinement}
+Let us denote by $A_{13}$ (resp.
+$A_{23}$) the open automaton resulting from $A_1\subst{A_3}{k}$ ($A_2\subst{A_3}{k}$),  to prove the theorem it sufficient to prove that there exists a relation between states of the two open automata that satisfies the conditions of the Definition \ref{Def:OA-Refinement}.
+Let $R$ be the refinement relation relating states of $A_1$ and $A_2$.\\
+Let us define $R'$ the relation:
+\[R' \mpar{\mpar{s_{13}, s'_{13}}, \mpar{s_{23}, s_{23}'}} = \choice{R\mpar{s_{13}, s_{23}} \wedge \reach{A_{13}}\mpar{s_{13},s_{13}'} \wedge\!\!\!\! \bigwedge_\subbox{\begin{array}{c}
+v\in \fvars{s'_{13}}\\
+v\in V_3
+\end{array}}\!\!\! \sigma_{13}(v)=\sigma_{23}(v) & \text{ if } s'_{13} = s'_{23} \\ \bot & \text{otherwise}} \]
+We want to prove that $\mpar{R, H\cup J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$.
+\begin{enumerate}
+\item By using the fact $R$ relates initial configurations of  $A_1$ and $A_2$, initial state is reachable and renaming $\sigma_{03}$ by  $\sigma_{013}$ and  $\sigma_{023}$ we need to prove:
+\[\sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}\]
+
+We have by hypothesis:
+\begin{align*}
+& \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
+\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
+\iff & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \wedge \bigwedge_\subbox{\begin{array}{c}
+v\in V_3
+\end{array}} \sigma_{03}(v)=\sigma_{03}(v)\\
+\iff & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \wedge \bigwedge_\subbox{\begin{array}{c}
+v\in V_3
+\end{array}} \sigma_{013}(v)=\sigma_{023}(v)
+\end{align*}
+
+\end{enumerate}
+
+\[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{J_3 \uplus H \setminus \mbrc{k}}\].
 

### 2021-12-17 2021-Refinement/paper/refinementarticle.tex
proof thm2 progress

@@
 \TODO{peut etre echanger c et p? ou c devient p et p devient? }
-\begin{definition}[Composition of open automata]
+\begin{definition}[Composition of open automata] \label{Def:CompOA}
 The composition of \(A_c = \OAg[c]\) in the hole \(k \in J_p\) of \(A_p = \OAg[p]\) is the OA defined as follows:
@@
 Let $R$ be the refinement relation relating states of $A_1$ and $A_2$.\\
-Let us define $R'$ the relation:
-\[R' \mpar{\mpar{s_{13}, s'_{13}}, \mpar{s_{23}, s_{23}'}} = \choice{R\mpar{s_{13}, s_{23}} \wedge \reach{A_{13}}\mpar{s_{13},s_{13}'} \wedge\!\!\!\! \bigwedge_\subbox{\begin{array}{c}
-v\in \fvars{s'_{13}}\\
-v\in V_3
-\end{array}}\!\!\! \sigma_{13}(v)=\sigma_{23}(v) & \text{ if } s'_{13} = s'_{23} \\ \bot & \text{otherwise}} \]
-We want to prove that $\mpar{R, H\cup J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$.
+Let us consider any two states $s_{13} = \mpar{s_1,s_3}$ and $s_{23} = \mpar{s_2,s_3'}$ we define a relation $R'$ relating states of $A_{13}$ and $A_{23}$ as follows:
+\[R' \mpar{s_{13}, s_{23}} = \choice{R\mpar{s_{1}, s_{2}} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge\!\!\!\! \bigwedge_\subbox{v\in \fvars{s_{3}}
+}\!\!\! \sigma_{13}(v)=\sigma_{23}(v) & \text{ if } s_{3} = s'_{3} \\ \bot & \text{otherwise}} \]
+We want to prove that $\mpar{R', H\cup J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$.
 \begin{enumerate}
-\item By using the fact $R$ relates initial configurations of  $A_1$ and $A_2$, initial state is reachable and renaming $\sigma_{03}$ by  $\sigma_{013}$ and  $\sigma_{023}$ we need to prove:
+\item By using the fact $R$ relates initial configurations of  $A_1$ and $A_2$, initial states are reachable and by renaming $\sigma_{03}$ by  $\sigma_{013}$ and  $\sigma_{023}$ we need to prove:
 \[\sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}\]
@@
 \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
-\iff & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \wedge \bigwedge_\subbox{\begin{array}{c}
-v\in V_3
-\end{array}} \sigma_{03}(v)=\sigma_{03}(v)\\
-\iff & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \wedge \bigwedge_\subbox{\begin{array}{c}
-v\in V_3
-\end{array}} \sigma_{013}(v)=\sigma_{023}(v)
+\iff & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \wedge \bigwedge_\subbox{v\in V_3} \sigma_{03}(v)=\sigma_{03}(v)\\
+\iff & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \wedge \bigwedge_\subbox{v\in V_3} \sigma_{013}(v)=\sigma_{023}(v)\\
+\iff & R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v\in V_3} \sigma_{013}(v)=\sigma_{023}(v) \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma_{013} \uplus \sigma_{023}}
 \end{align*}
+\item We need to prove for any OT $t_{13}$ originating from $s_{13}$:
+\begin{align*}
+		&  \OTx{13}{}{13}{13} \in \fOT{s_{13}}
+\end{align*}		
+there exist an indexed family $t_{23x}$ of OTs originating from $s_{23}$: 
+\begin{align*}
+		&  \mpar{\OTx{23}{x}{23x}{23x} \in \fOT{s_{23}}}^{x \in X}
+\end{align*}	
+\begin{align*}		
+		& \quad \mpar{\forall x \in X, J'_{23x} \cap H = J'_{13} \cap H} \nwedge\\
+		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H} \beta_{13j} = \beta_{23xj} \\[12pt]
+			\nwedge g_{23x} \wedge R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
+		\end{array}} 
+	\end{align*}
+According to Definition \ref{Def:CompOA}, we know that $t_{13}$ is built by:
+ \[  \choice{
+	\OTx{1}{}{1}{1} \wedge  \OTx{3}{}{3}{3}
+	& \text{if } k \in J'_{1} \\
+	\OTx{1}{}{1}{1}	 & \text{otherwise}
+	} \]
+
+By hypothesis, we have for any open transition $t_1$ in $T_1$  originating from $s_1$:
+\begin{align*}
+\OTx{1}{}{1}{1} \in \fOT{s_1}
+\end{align*}
+there exist an indexed family of OTs originating from $s_{2}$: 
+\begin{align*}
+\mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_{2}}}^{x \in X} 
+\end{align*}
+such that $\forall x \in X, J'_{2x} \cap H = J'_1 \cap H$ and
+\begin{multline*}
+%\everymath{\displaystyle}
+V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\ \mpar{R\mpar{s_1, s_{2}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \nwedge\\
+			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}}} 
+\end{multline*}
 

### 2022-01-03 2021-Refinement/paper/refinementarticle.tex
Proof of lemm 2 in progress

@@
 Before characterising a composition which does not introduce deadlocks we need to be able to tell which states are reachable.
-\begin{definition}[Reachability]
+\begin{definition}[Reachability] \label{Def:Reach}
 For any open automata \(A = \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is any predicate on states that is valid on initial state, and preserved across transitions:
@@
 
+\begin{theorem}[Congruence]
+Let $A_1$, $A_2$ and $A_3$ be three open automata with $\wrel{A_2}{A_3}{H}$. 
+Suppose that \(k \in H\) and that \(A_1\subst{A_2}{k}\) is non-locking.
+We have: \[\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{J_1 \uplus H \setminus \mbrc{k}}\].
+\end{theorem}
 - composition is a refinement (under which condition? non-locking composition?)
@@
 Let $R$ be the refinement relation relating states of $A_1$ and $A_2$.\\
-Let us consider any two states $s_{13} = \mpar{s_1,s_3}$ and $s_{23} = \mpar{s_2,s_3'}$ we define a relation $R'$ relating states of $A_{13}$ and $A_{23}$ as follows:
+Let us consider any two states $s_{13} = \mpar{s_1,s_3}$ and $s_{23} = \mpar{s_2,q_3}$ we define a relation $R'$ relating states of $A_{13}$ and $A_{23}$ as follows:
 \[R' \mpar{s_{13}, s_{23}} = \choice{R\mpar{s_{1}, s_{2}} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge\!\!\!\! \bigwedge_\subbox{v\in \fvars{s_{3}}
-}\!\!\! \sigma_{13}(v)=\sigma_{23}(v) & \text{ if } s_{3} = s'_{3} \\ \bot & \text{otherwise}} \]
+}\!\!\! \sigma_{13}(v)=\sigma_{23}(v) & \text{ if } s_{3} = q_{3} \\ \bot & \text{otherwise}} \]
 We want to prove that $\mpar{R', H\cup J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$.
@@
 \end{align*}
-\item We need to prove for any OT $t_{13}$ originating from $s_{13}$:
+\item We need to prove for any OT $t_{13}$ in $T_{13}$ originating from $s_{13}$:
 \begin{align*}
@@
 \end{align*}		
-there exist an indexed family $t_{23x}$ of OTs originating from $s_{23}$: 
+there exists an indexed family $t_{23x}$ of OTs originating from $s_{23}$: 
 \begin{align*}
@@
 \begin{align*}		
-		& \quad \mpar{\forall x \in X, J'_{23x} \cap H = J'_{13} \cap H} \nwedge\\
-		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H} \beta_{13j} = \beta_{23xj} \\[12pt]
-			\nwedge g_{23x} \wedge R\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
+		& \text{such that } \mpar{\forall x \in X, J'_{23x} \cap H' = J'_{13} \cap H'} \text{ and }\\
+		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
+			\nwedge g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
 		\end{array}} 
 	\end{align*}
-According to Definition \ref{Def:CompOA}, we know that $t_{13}$ is built by:
- \[  \choice{
-	\OTx{1}{}{1}{1} \wedge  \OTx{3}{}{3}{3}
-	& \text{if } k \in J'_{1} \\
-	\OTx{1}{}{1}{1}	 & \text{otherwise}
-	} \]
+where 
+\begin{align*}
+&V_{13}= V_1\uplus V_3 \text{ and }
+V_{23}= V_2\uplus V_3\\
+& H'=J_3'\uplus H \setminus \{k\} \subseteq J_3'\uplus \mpar{J_1' \cap J_2'} \setminus \{k\} = \mpar{J_3'\uplus J_1' \setminus \{k\} } \cap \mpar{J_3'\uplus J_2' \setminus \{k\}} = J_{13}'\cap J_{12}'\\
+\end{align*}
+The open transition $t_{13}$ is obtained by the composition of $t_1=\OTx{1}{}{1}{1}$ and $t_3=\OTx{3}{}{3}{3} $, which gives,  according to Definition \ref{Def:CompOA}, an open transition in one of the following forms:
+% \[  \choice{
+%	\OTx{1}{}{1}{1} \text{ and }  \OTx{3}{}{3}{3}
+%	& \text{if } k \in J'_{1} \\
+%	\OTx{1}{}{1}{1}	 & \text{otherwise}
+%	} \]
+\[
+\choice{
+\OT{\mpar{s_1, s_3}}{\mpar{s'_1, s'_3}}{\alpha_1}{\beta_j^{j \in J'_1 \uplus J'_3 \setminus \{k\}}}{g_1 \wedge g_3 \wedge \alpha_3 = \beta_k}{\psi_1 \uplus \psi_3} & \text{ if } k \in J'_{1} \\
+\OT{\mpar{s_1, s_3}}{\mpar{s'_1, s_3}}{\alpha_1}{\beta_j^{j \in J'_1}}{g_1}{\psi_1}& \text{otherwise}
+}
+\]
 
-By hypothesis, we have for any open transition $t_1$ in $T_1$  originating from $s_1$:
+We have by hypothesis $\wrel{A_1}{A_2}{H}$, then for any open transition $t_1$ in $T_1$  originating from $s_1$:
 \begin{align*}
@@
 \end{align*}
-there exist an indexed family of OTs originating from $s_{2}$: 
+there exists an indexed family of OTs originating from $s_{2}$: 
 \begin{align*}
@@
 			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}}} 
+		\end{array}}}  \qquad (*)
 \end{multline*}	
+We have  $k \in H$ and $k \in J'_{1}$ then  we have $k \in J'_{2x}$.\\
+By composing the family of OTs  $t_{2x}^{x\in X}$ originating from  $s_2$ with an open transition $t_3 =\OT{q_3}{q_3'}{\alpha_{3}'}{\beta_j^{j \in J''_{3}}}{g_{3}'}{\psi_{3}'} \in T_3$ %${\OT{q_{3}}{q'_{3}}{\alpha_{3}}{\beta_{ j}^{j \in J'_{3}}}{g_{3}}{\psi_{3}}}$,
+gives a family of OTs $t_{23x}^{x\in X}$.  The result of the composition will be as follows:
+\begin{enumerate}
+\item if $ s_3=q_3$
+\[
+\choice{
+\OT{\mpar{s_2, q_3}}{\mpar{s'_{2x}, q'_3}}{\alpha_{2x}}{\beta_j^{j \in J'_{2x} \uplus J''_3 \setminus \{k\}}}{g_{2x} \wedge g_3' \wedge \alpha_3' = \beta_{2xk}}{\psi_{2x} \uplus \psi_3'} & \text{ if } k \in J'_{2x} \\
+\OT{\mpar{s_2, q_3}}{\mpar{s'_{2x}, q_3}}{\alpha_{2x}}{\beta_j^{j \in J'_{2x}}}{g_{2x}}{\psi_{2x}}& \text{otherwise}
+}
+\]
+\item if $s_3 \neq q_3$ no element is produced that results an empty family.
+\end{enumerate}
+
+It remains to prove that we have:
+\begin{align*}		
+		&\mpar{\forall x \in X, J'_{23x} \cap H' = J'_{13} \cap H'} \text{ and }\\
+		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
+			\nwedge g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
+		\end{array}} 
+	\end{align*}
+
+For all $x \in X$ we have two cases:
+\begin{align*}
+		\text{if } k \in J'_1: && J'_{23x} \cap H' & = \mpar{J'_{3} \uplus J'_{2x} \setminus \mbrc{k}} \cap  \mpar{J'_{3} \uplus H \setminus \mbrc{k}}\\
+		&&& = J'_{3}  \uplus \mpar{J'_{2x} \cap H} \setminus \mbrc{k} \\
+		&&& = J'_{3} \uplus \mpar{J'_1 \cap H} \setminus \mbrc{k} \\
+		&&& = \mpar{ J'_{3} \uplus J'_1 \setminus \mbrc{k}} \cap \mpar{J'_{3} \uplus H \setminus \mbrc{k}}\\
+		&&& = J'_{13} \cap H'\\
+\text{if } k \notin J'_1: && J'_{23x} \cap H' & = \mpar{J'_{2x} \setminus \mbrc{k}} \cap \mpar{J'_3 \uplus H \setminus \mbrc{k}} \\
+		&&& = \mpar{J'_{2x} \cap H} \setminus \mbrc{k} \\
+		&&& = \mpar{J'_1 \cap H} \setminus \mbrc{k}  \\
+		&&& = J'_3 \uplus \mpar{J'_1 \cap H} \setminus \mbrc{k}  \\
+		&&& = J'_{13} \cap H'
+		\end{align*}
+
+By hypothesis $\reach{A_{13}}\mpar{s_{13}}$ holds,  we then have according to the Definition \ref{Def:Reach} the following:
+\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
+\TODO{Un peu de gymnastique est necessaire sur les valuations, etc...}
+From this formula and $(*)$ 
+\begin{multline*}
+%\everymath{\displaystyle}
+V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1} \vdash\\ \mpar{R\mpar{s_1, s_{2}} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge g_{13} 
+\wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \nwedge\\
+			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}}} \wedge \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}
+\end{multline*}
+
+\TODO{Pas termine: valider d'abord la definition de R}
+\item The last formula to prove is the following:
+\begin{multline*}
+\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23},\\ V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_2} \vdash \left(R\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_1 \in \fOT{s_{13}}} \fguard{t_{13}} \right)
+\end{multline*}
+By hypothesis we have the following:
+\begin{multline*}
+\forall \mpar{s_1, s_2} \in S_1 \times S_2,\\ V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
+\end{multline*}
+By adding the term $\displaystyle{\bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3}}$ to both sides of the implication, we get: 
+\begin{multline*}
+\forall \mpar{s_1, s_2,s_3} \in S_1 \times S_2 \times S_3, V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3}\right)
+\end{multline*}
+By hypothesis we also have \(A_1\subst{A_3}{k}\) is non-locking,  thus we can write the following:
+\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]
 
@@
 
-\[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{J_3 \uplus H \setminus \mbrc{k}}\].
+%\[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{J_3 \uplus H \setminus \mbrc{k}}\].
 

### 2022-01-06 2021-Refinement/paper/refinementarticle.tex
added Relations between open automata

@@
 The action emitted when \(A_c\) makes a transition is synchronised with the action of the hole \(k\) in transitions of \(A_p\) .
+
+\paragraph{Relations between open automata}
+A relation (bisimulation, refinement, etc.) between open automata requires to compare their states.
+To do so we will suppose that the variables of the two OAs are disjoint (a renaming of variables may have to be applied before comparing OA states)
+\begin{definition}[Relation on OA states] Suppose $V_1$ and $V_2$ are disjoint.
+A relation on states of \(\OAg[1]\) and \(\OAg[2]\) is a function \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
+\end{definition}
+The idea is that two states are related if the variables they refer to verify a certain formula.
+Additionally, we may check that initial states of the automata are related by checking that: \(\sigma_{01} \uplus \sigma_{022} \vdash R\mpar{s_{01}, s_{02}}\).
+
+\TODO{I do not think we reason on configurations for the moment, if we want to, we should introduce this:}
+Two configurations \(\mpar{s_1, \sigma_1} \in S_1 \mpar{V_1 \to \values}, \mpar{s_2, \sigma_2} \in S_2 \times \mpar{V_2 \to \values}\) are related iff \(\sigma_1 \uplus \sigma_2 \vdash R\mpar{s_1, s_2}\).
 

### 2022-01-12 2021-Refinement/paper/refinementarticle.tex
proof suite

@@
 \TODO{I do not think we reason on configurations for the moment, if we want to, we should introduce this:}
-Two configurations \(\mpar{s_1, \sigma_1} \in S_1 \mpar{V_1 \to \values}, \mpar{s_2, \sigma_2} \in S_2 \times \mpar{V_2 \to \values}\) are related iff \(\sigma_1 \uplus \sigma_2 \vdash R\mpar{s_1, s_2}\).
+Two configurations \(\mpar{s_1, \sigma_1} \in S_1 \times\mpar{V_1 \to \values}, \mpar{s_2, \sigma_2} \in S_2 \times \mpar{V_2 \to \values}\) are related iff \(\sigma_1 \uplus \sigma_2 \vdash R\mpar{s_1, s_2}\).
 
@@
 $\forall z \in Z,  J'_1 \cap (H \cap H') = J'_{3z} \cap (H\cap H')$\\
-$\displaystyle {\forall v \in \mpar{\fvars{\alpha_{1}}  \cup\!\!\! \bigcup_{j \in J'_{3z} \cap H \cap H'} \!\!\!\fvars{\beta_{1j} } } \setminus  \mpar{V_1 \uplus  V_3 \uplus \fvars{t_1}}} ,  $
+$\displaystyle {\forall v \in \mpar{\fvars{\alpha_{1}}  \cup\!\!\! \bigcup_{j \in J'_{3z} \cap H \cap H'} \!\!\!\fvars{\beta_{1j} } } \setminus  \mpar{V_1 \uplus  V_3 \uplus \fvars{t_1}}},$
 \begin{align*}
@@
 Let $R$ be the refinement relation relating states of $A_1$ and $A_2$.\\
-Let us consider any two states $s_{13} = \mpar{s_1,s_3}$ and $s_{23} = \mpar{s_2,q_3}$ we define a relation $R'$ relating states of $A_{13}$ and $A_{23}$ as follows:
-\[R' \mpar{s_{13}, s_{23}} = \choice{R\mpar{s_{1}, s_{2}} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge\!\!\!\! \bigwedge_\subbox{v\in \fvars{s_{3}}
-}\!\!\! \sigma_{13}(v)=\sigma_{23}(v) & \text{ if } s_{3} = q_{3} \\ \bot & \text{otherwise}} \]
+Let us consider any two states $s_{13} = \mpar{s_1,s^1_3}$ and $s_{23} = \mpar{s_2,s^2_3}$ ($s^1_3$ and $s^2_3$  are same with renaming).
+We define a relation $R'$ relating states of $A_{13}$ and $A_{23}$ as follows:
+\[ R' \mpar{s_{13}, s_{23}} = R\mpar{s_{1}, s_{2}} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge s^1_3 = s^2_3\]
+
+\TODO{Old version \[R' \mpar{s_{13}, s_{23}} = \choice{R\mpar{s_{1}, s_{2}} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge\!\!\!\! \bigwedge_\subbox{v\in \fvars{s_{3}}
+}\!\!\! \sigma_{13}(v)=\sigma_{23}(v) & \text{ if } s_{3} = q_{3} \\ \bot & \text{otherwise}} \]}
 We want to prove that $\mpar{R', H\cup J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$.
@@
 \end{align*}
-The open transition $t_{13}$ is obtained by the composition of $t_1=\OTx{1}{}{1}{1}$ and $t_3=\OTx{3}{}{3}{3} $, which gives,  according to Definition \ref{Def:CompOA}, an open transition in one of the following forms:
-% \[  \choice{
-%	\OTx{1}{}{1}{1} \text{ and }  \OTx{3}{}{3}{3}
-%	& \text{if } k \in J'_{1} \\
-%	\OTx{1}{}{1}{1}	 & \text{otherwise}
-%	} \]
-\[
-\choice{
-\OT{\mpar{s_1, s_3}}{\mpar{s'_1, s'_3}}{\alpha_1}{\beta_j^{j \in J'_1 \uplus J'_3 \setminus \{k\}}}{g_1 \wedge g_3 \wedge \alpha_3 = \beta_k}{\psi_1 \uplus \psi_3} & \text{ if } k \in J'_{1} \\
-\OT{\mpar{s_1, s_3}}{\mpar{s'_1, s_3}}{\alpha_1}{\beta_j^{j \in J'_1}}{g_1}{\psi_1}& \text{otherwise}
-}
-\]
+
+\medskip
 
@@
 \end{multline*}	
+\smallskip
+
+The open transition $t_{13}$ is obtained by the composition of $t_1=\OTx{1}{}{1}{1}$ and $t_3=\OTx{3}{}{3}{3} $, that gives,  according to Definition \ref{Def:CompOA}, an open transition in one of the following forms:
+% \[  \choice{
+%	\OTx{1}{}{1}{1} \text{ and }  \OTx{3}{}{3}{3}
+%	& \text{if } k \in J'_{1} \\
+%	\OTx{1}{}{1}{1}	 & \text{otherwise}
+%	} \]
+\[
+\choice{
+\OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, {s^1_3}'}}{\alpha_1}{\beta_j^{j \in J'_1 \uplus J'_3 \setminus \{k\}}}{g_1 \wedge g_3 \wedge \alpha_3 = \beta_{1k}}{\psi_1 \uplus \psi_3} & \text{ if } k \in J'_{1} \\
+\OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, s^1_3}}{\alpha_1}{\beta_j^{j \in J'_1}}{g_1}{\psi_1}& \text{otherwise}
+}
+\]
+
 We have  $k \in H$ and $k \in J'_{1}$ then  we have $k \in J'_{2x}$.\\
-By composing the family of OTs  $t_{2x}^{x\in X}$ originating from  $s_2$ with an open transition $t_3 =\OT{q_3}{q_3'}{\alpha_{3}'}{\beta_j^{j \in J''_{3}}}{g_{3}'}{\psi_{3}'} \in T_3$ %${\OT{q_{3}}{q'_{3}}{\alpha_{3}}{\beta_{ j}^{j \in J'_{3}}}{g_{3}}{\psi_{3}}}$,
+By composing the family of OTs  $t_{2x}^{x\in X}$ originating from  $s_2$ with an open transition $t_3=\OTx{3}{}{3}{3} \in T_3$
+%$t_3 =\OT{q_3}{q_3'}{\alpha_{3}'}{\beta_j^{j \in J''_{3}}}{g_{3}'}{\psi_{3}'} \in T_3$ %${\OT{q_{3}}{q'_{3}}{\alpha_{3}}{\beta_{ j}^{j \in J'_{3}}}{g_{3}}{\psi_{3}}}$, 
 gives a family of OTs $t_{23x}^{x\in X}$.  The result of the composition will be as follows:
 \begin{enumerate}
-\item if $ s_3=q_3$
+\item if $ s^1_3=s^2_3$
 \[
 \choice{
-\OT{\mpar{s_2, q_3}}{\mpar{s'_{2x}, q'_3}}{\alpha_{2x}}{\beta_j^{j \in J'_{2x} \uplus J''_3 \setminus \{k\}}}{g_{2x} \wedge g_3' \wedge \alpha_3' = \beta_{2xk}}{\psi_{2x} \uplus \psi_3'} & \text{ if } k \in J'_{2x} \\
-\OT{\mpar{s_2, q_3}}{\mpar{s'_{2x}, q_3}}{\alpha_{2x}}{\beta_j^{j \in J'_{2x}}}{g_{2x}}{\psi_{2x}}& \text{otherwise}
+\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, {s^2_3}'}}{\alpha_{2x}}{\beta_j^{j \in J'_{2x} \uplus J'_3 \setminus \{k\}}}{g_{2x} \wedge g_3 \wedge \alpha_3 = \beta_{2xk}}{\psi_{2x} \uplus \psi_3} & \text{ if } k \in J'_{2x} \\
+\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, s^2_3}}{\alpha_{2x}}{\beta_j^{j \in J'_{2x}}}{g_{2x}}{\psi_{2x}}& \text{otherwise}
 }
 \]
-\item if $s_3 \neq q_3$ no element is produced that results an empty family.
+\item if $s^1_3 \neq s^2_3$ no element is produced that results an empty family.
 \end{enumerate}
@@
 
-By hypothesis $\reach{A_{13}}\mpar{s_{13}}$ holds,  we then have according to the Definition \ref{Def:Reach} the following:
-\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
-\TODO{Un peu de gymnastique est necessaire sur les valuations, etc...}
-From this formula and $(*)$ 
+\smallskip
+
+By adding the same terms to both sides of the implication of the  formula $(*)$, we get:
+
+\begin{itemize}
+\item In the case $ s^1_3=s^2_3$ and $k \in J'_1$:\\
+$\displaystyle {\forall v \in \mpar{\fvars{\alpha_{1}}  \cup\!\!\! \bigcup_{j \in J'_{2x}} \!\!\!\fvars{\beta_{1j} } } \setminus  \mpar{V_1 \uplus  V_2 \uplus \fvars{t_1}}},$
 \begin{multline*}
-%\everymath{\displaystyle}
-V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1} \vdash\\ \mpar{R\mpar{s_1, s_{2}} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge g_{13} 
-\wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+R\mpar{s_1, s_{2}} \wedge g_1 \wedge g_3 \wedge \alpha_3=\beta_{1k} \wedge s^1_3=s^2_3\implies\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
 \begin{array}{l}
@@
 			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}}} \wedge \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}
+		\end{array}}  \wedge g_3 \wedge \alpha_3=\beta_{1k} \wedge s^1_3=s^2_3
+\end{multline*}	
+Based on the fact that the composition doesn't change the resulting actions, nor the variables, and on the fact that for $k \in H$ we have $\beta_{1k}=\beta_{2xk}$, the we get after simplification:
+\begin{multline*}
+R\mpar{s_1, s_{2}} \wedge g_{13} \wedge s^1_3=s^2_3\implies\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H} \beta_{1j} = \beta_{2xj} \nwedge\\
+			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}}  \wedge g_3 \wedge \alpha_3=\beta_{1k} \wedge s^1_3=s^2_3
 \end{multline*}
 
+By hypothesis $\reach{A_{13}}\mpar{s_{13}}$ holds,  we then have according to the Definition \ref{Def:Reach} the following:
+\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
+\end{itemize}
 \TODO{Pas termine: valider d'abord la definition de R}

### 2022-01-25 2021-Refinement/paper/refinementarticle.tex
proof in progress
proof in progess

@@
 \end{align*}
-Yet according to the relation between $A_1$ and $A_2$ we have  forall $\mpar{s_1, s_{2p}} \in S_1 \times S_2$:
+Yet according to the relation between $A_1$ and $A_2$ we have  for all $\mpar{s_1, s_{2p}} \in S_1 \times S_2$:
 \begin{multline*}
@@
 \everymath{\displaystyle}
-\forall v\in \mpar{\fvars{\alpha_{2px}}  \cup \!\! \bigcup_{\begin{array}{c} p\in P\\ j \in J'_{2p}
+\forall v\in \mpar{\fvars{\alpha_{2px}}  \cup  \bigcup_{\begin{array}{c} \subbox{p\in P}\\ \subbox{j \in J'_{2p}}
 \end{array}} \!\! \fvars{\beta_{2pxj}}}\cup \mpar{\fvars{\alpha_{1}}  \cup\!\! \bigcup_{j \in J'_{1}} \!\!\fvars{\beta_{1j}}}
@@
 $A_{23}$) the open automaton resulting from $A_1\subst{A_3}{k}$ ($A_2\subst{A_3}{k}$),  to prove the theorem it sufficient to prove that there exists a relation between states of the two open automata that satisfies the conditions of the Definition \ref{Def:OA-Refinement}.
-Let $R$ be the refinement relation relating states of $A_1$ and $A_2$.\\
-Let us consider any two states $s_{13} = \mpar{s_1,s^1_3}$ and $s_{23} = \mpar{s_2,s^2_3}$ ($s^1_3$ and $s^2_3$  are same with renaming).
+The proof requires to resort to rename the elements (states, variables, etc) of an automaton according to the one to which they belong.
+
+Let $R$ be the refinement relation relating states of $A_1$ and $A_2$.
+Let us consider any two states $s_{13} = \mpar{s_1,s^1_3}$ and $s_{23} = \mpar{s_2,s^2_3}$ ($s^1_3$ and $s^2_3$  are the same with renaming).
 We define a relation $R'$ relating states of $A_{13}$ and $A_{23}$ as follows:
-\[ R' \mpar{s_{13}, s_{23}} = R\mpar{s_{1}, s_{2}} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge s^1_3 = s^2_3\]
+\[ R' \mpar{s_{13}, s_{23}} = R\mpar{s_{1}, s_{2}} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigwedge_\subbox{v_3\in \fvars{s_{3}}
+}\!\!\! v^1_3=v^2_3\wedge s^1_3 = s^2_3\]
 
-\TODO{Old version \[R' \mpar{s_{13}, s_{23}} = \choice{R\mpar{s_{1}, s_{2}} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge\!\!\!\! \bigwedge_\subbox{v\in \fvars{s_{3}}
-}\!\!\! \sigma_{13}(v)=\sigma_{23}(v) & \text{ if } s_{3} = q_{3} \\ \bot & \text{otherwise}} \]}
 We want to prove that $\mpar{R', H\cup J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$.
 \begin{enumerate}
-\item By using the fact $R$ relates initial configurations of  $A_1$ and $A_2$, initial states are reachable and by renaming $\sigma_{03}$ by  $\sigma_{013}$ and  $\sigma_{023}$ we need to prove:
+\item First, we have to prove:
 \[\sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}\]
 
-We have by hypothesis:
+By using the fact that $R$ relates initial configurations of  $A_1$ and $A_2$, we have  the following statement holds:
+$\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}}$.
+And secondly, because the domain of the substitution function is disjoint from the others, it has an effect only on the related elements, and relying on the  fact that initial states are reachable we  have:
 \begin{align*}
@@
 \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
-\iff & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \wedge \bigwedge_\subbox{v\in V_3} \sigma_{03}(v)=\sigma_{03}(v)\\
-\iff & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \wedge \bigwedge_\subbox{v\in V_3} \sigma_{013}(v)=\sigma_{023}(v)\\
-\iff & R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v\in V_3} \sigma_{013}(v)=\sigma_{023}(v) \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma_{013} \uplus \sigma_{023}}
+\iff & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \wedge\underbrace{  \bigwedge_\subbox{v_3\in V_3} \sigma^1_{03}(v^1_3)=\sigma^2_{03}(v^2_3)\wedge s^1_3 = s^2_3}_{\Longleftrightarrow~\top}\\
+\iff & \mpar{R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma_{013} \uplus \sigma^1_{03}\uplus \sigma^2_{03} }\\
+\iff & \sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}
 \end{align*}
+
 \item We need to prove for any OT $t_{13}$ in $T_{13}$ originating from $s_{13}$:
@@
 \begin{align*}
-&V_{13}= V_1\uplus V_3 \text{ and }
-V_{23}= V_2\uplus V_3\\
+&V_{13}= V_1\uplus V^1_3 \text{ and }
+V_{23}= V_2\uplus V^2_3\\
 & H'=J_3'\uplus H \setminus \{k\} \subseteq J_3'\uplus \mpar{J_1' \cap J_2'} \setminus \{k\} = \mpar{J_3'\uplus J_1' \setminus \{k\} } \cap \mpar{J_3'\uplus J_2' \setminus \{k\}} = J_{13}'\cap J_{12}'\\
@@
 			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}}}  \qquad (*)
+		\end{array}}}  \qquad \quad (*)
 \end{multline*}	
 \smallskip
+Consider any transition $t_{13}$ in $A_{13}$,  $t_{13}$ is obtained either by the composition of the transition $t_1=\OTx{1}{}{1}{1}$ and the transition %$t_3^1=\OTxup{3}{1} $, if $k \in J_1'$; or by the transition $t_1$ and the state $s_3^1$, otherwise (if $k \notin J_1'$).
+%%%% Attention deactiver ici
+\[
+\choice{
+\OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, {s^1_3}'}}{\alpha_1}{\beta_{1j}^{j \in J'_1 \setminus \{k\}} \uplus  {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{g_1 \wedge g^1_3 \wedge \alpha^1_3 = \beta_{1k}}{\psi_1 \uplus \psi^1_3} & \text{ if } k \in J'_{1} \\
+\OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, s^1_3}}{\alpha_1}{\beta_{1j}^{j \in J'_1}}{g_1}{\psi_1}& \text{otherwise}
+}
+\]
 
-The open transition $t_{13}$ is obtained by the composition of $t_1=\OTx{1}{}{1}{1}$ and $t_3=\OTx{3}{}{3}{3} $, that gives,  according to Definition \ref{Def:CompOA}, an open transition in one of the following forms:
+\medskip
+
+By hypothesis we have $k \in H$, so in the case where $k \in J'_{1}$, we deduce that $k \in J'_{2x}$ we can  then build  a family of OTs $t_{23x}^{x\in X}$ with the same transitions of $A_3$ (up to renaming) as those used to build $t_{13}$.
+For any $t_{23x}$  there will then be two cases according on how it is built:
+
+\[
+\choice{
+\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, {s^2_3}'}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }}{g_{2x} \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2xk}}{\psi_{2x} \uplus \psi^2_3} & \text{ if } k \in J'_{2x} \\
+\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, s^2_3}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x}}}{g_{2x}}{\psi_{2x}}& \text{otherwise}
+}
+\]
+
+So have to prove the following:
+\begin{align*}		
+		&\mpar{\forall x \in X, J'_{23x} \cap H' = J'_{13} \cap H'} \text{ and }\\
+		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
+			\nwedge g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
+		\end{array}} 
+	\end{align*}
+
+For all $x \in X$ we have to consider both  cases:
+\begin{align*}
+	\text{if } k \in J'_1:\quad &  J'_{23x} \cap H'  = 
+	\mpar{ J'_{2x}\uplus J^{2 \prime}_{3}  \setminus \mbrc{k}} \cap  \mpar{J^{2 \prime}_{3} \uplus H \setminus \mbrc{k}} \\
+		& = J^{2 \prime}_{3}  \uplus \mpar{J'_{2x} \cap H} \setminus \mbrc{k} \quad \text{ since } J^{1 \prime}_{3}=J^{2 \prime}_{3} \text{ and } J'_1 \cap H = J'_{2x} \cap H\\
+		& = J^{1 \prime}_{3} \uplus \mpar{J'_1 \cap H} \setminus \mbrc{k} \\
+		& = \mpar{ J'_1  \uplus J^{1 \prime}_{3}\setminus \mbrc{k}} \cap \mpar{J^{1 \prime}_{3} \uplus H \setminus \mbrc{k}}\\
+		& = J'_{13} \cap H'\\
+\text{if } k \notin J'_1:\quad &	J'_{23x} \cap H'  = \mpar{J'_{2x} \setminus \mbrc{k}} \cap \mpar{J^{2 \prime}_3 \uplus H \setminus \mbrc{k}} \\
+\end{align*}
+
+For the rest of the formula we will also consider the two cases separately.
+
+\begin{itemize}
+\item If $k \in J'_1$: we will extend the valuation context of the variables to cover the variables of the transition $t_3$.
+Based on this fact we have: $ \alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$ because composition doesn't change the resulting actions, nor their variables.
+We also have 
+${\displaystyle \bigwedge_\subbox{j \in J'_{23x} \cap H} \beta_{1j} = \beta_{2xj} \Rightarrow  \bigwedge_\subbox{j \in J'_{23x} \cap H} \beta_{13j} = \beta_{23xj}}$ since the actions of the holes in $J_3$ coincide on both sides.
+And the following statements:
+$g_{13} \Leftrightarrow g_1 \wedge g_3 \wedge \alpha_3=\beta_{1k}$, 
+$g_{23x}  \Leftrightarrow g_{2x} \wedge g_3 \wedge \alpha_3=\beta_{2xk}$ and $\beta_{1k} = \beta_{2xk}$\\
+
+From the formula $(*)$ to which we have added the same terms ($g_3 \wedge \alpha_3=\beta_{1k} {\displaystyle \wedge\bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3}$) to both sides of the implication and from all the points mentioned above, we get:\\
+
+$\displaystyle {\forall v \in \mpar{\fvars{\alpha_{13}}  \cup\!\!\!
+\bigcup_{j \in J'_{23x}} \!\!\!\fvars{\beta_{13j} } } \setminus  \mpar{V_1 \uplus  V_2  \uplus V_3 \uplus  \fvars{t_1} \uplus \fvars{t_3}}},$
+\begin{multline*}
+R\mpar{s_1, s_{2}} \wedge g_1 \wedge g_3 \wedge \alpha_3=\beta_{1k} \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3\implies\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{13j} = \beta_{23xj} \nwedge\\
+			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}}  \wedge g_3 \wedge \alpha_3=\beta_{2xk} \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s'^1_3=s'^2_3
+\end{multline*}	
+That can be re-written as follows:
+\begin{multline*}
+R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3\implies\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{13j} = \beta_{23xj} \nwedge\\
+			 g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s'^1_3=s'^2_3
+		\end{array}}   
+\end{multline*}
+
+By hypothesis $\reach{A_{13}}\mpar{s_{13}}$ holds,  we then have according to the Definition \ref{Def:Reach} the following:
+\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
+\end{itemize}
+
+\newpage
+%%%%%%%%%%%%%%%%%%%%%%%%%%%555
+
+ that gives,  according to Definition \ref{Def:CompOA}
+
+The open transition $t_{13}$ is obtained by the composition of $t_1=\OTx{1}{}{1}{1}$ and $t_3=\OTx{3^1}{}{3}{3}$, that gives,  according to Definition \ref{Def:CompOA}, an open transition in one of the following forms:
 % \[  \choice{
@@
 \[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
-
 \end{enumerate}

### 2022-01-26 2021-Refinement/paper/refinementarticle.tex
trying to progress on proof ...  abit lost

@@
 $\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}}$.
-And secondly, because the domain of the substitution function is disjoint from the others, it has an effect only on the related elements, and relying on the  fact that initial states are reachable we  have:
+And secondly, because the domain of the substitution function is disjoint from the others, it has an effect only on the related elements, and relying on the  fact that initial states are reachable we  have:\TODO{define states and assignments}
 \begin{align*}
@@
 \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
-\iff & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \wedge\underbrace{  \bigwedge_\subbox{v_3\in V_3} \sigma^1_{03}(v^1_3)=\sigma^2_{03}(v^2_3)\wedge s^1_3 = s^2_3}_{\Longleftrightarrow~\top}\\
-\iff & \mpar{R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma_{013} \uplus \sigma^1_{03}\uplus \sigma^2_{03} }\\
-\iff & \sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}
+\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \wedge\underbrace{  \bigwedge_\subbox{v_3\in V_3} \sigma^1_{03}(v^1_3)=\sigma^2_{03}(v^2_3)\wedge s^1_3 = s^2_3}_{\Longleftrightarrow~\top?????}\\
+\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma_{013} \uplus \sigma^1_{03}\uplus \sigma^2_{03} }\\
+\implies & \sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}
 \end{align*}
@@
 \smallskip
-Consider any transition $t_{13}$ in $A_{13}$,  $t_{13}$ is obtained either by the composition of the transition $t_1=\OTx{1}{}{1}{1}$ and the transition %$t_3^1=\OTxup{3}{1} $, if $k \in J_1'$; or by the transition $t_1$ and the state $s_3^1$, otherwise (if $k \notin J_1'$).
+Consider any transition $t_{13}$ in $A_{13}$,  $t_{13}$ is obtained (by case analysis on the definition of composition)
+
+* either by the composition of a transition $t_1=\OTx{1}{}{1}{1}$ and a transition \[t_3^1=
+\OT{ s^1_3}{{s^1_3}'}{\alpha_3^1}{ \uplus  {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{ g^1_3 }{ \psi^1_3} \qquad \text{ when } k \in J'_{1} 
+\]. We obtain:
 %%%% Attention deactiver ici
 \[
-\choice{
-\OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, {s^1_3}'}}{\alpha_1}{\beta_{1j}^{j \in J'_1 \setminus \{k\}} \uplus  {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{g_1 \wedge g^1_3 \wedge \alpha^1_3 = \beta_{1k}}{\psi_1 \uplus \psi^1_3} & \text{ if } k \in J'_{1} \\
-\OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, s^1_3}}{\alpha_1}{\beta_{1j}^{j \in J'_1}}{g_1}{\psi_1}& \text{otherwise}
-}
+\OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, {s^1_3}'}}{\alpha_1}{\beta_{1j}^{j \in J'_1 \setminus \{k\}} \uplus  {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{g_1 \wedge g^1_3 \wedge \alpha^1_3 = \beta_{1k}}{\psi_1 \uplus \psi^1_3} \qquad \text{ where } k \in J'_{1}
 \]
 
+* or by an the transition $t_1=\OTx{1}{}{1}{1}$ alone with the state $s^1_3$ unchanged, if $k \not\in J_1'$
+\[\OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, s^1_3}}{\alpha_1}{\beta_{1j}^{j \in J'_1}}{g_1}{\psi_1}
+\]
 \medskip

### 2022-01-27 2021-Refinement/paper/refinementarticle.tex
push rule factoorisation
work with rab

@@
 Let $A_1$, $A_2$ and $A_3$ be three open automata with $\wrel{A_1}{A_2}{H}$. 
+Let $J_3$ be the set of holes of $A_3$.
 Suppose that \(k \in H\) and that \(A_1\subst{A_3}{k}\) is non-locking.
@@
 
-We want to prove that $\mpar{R', H\cup J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$.
+We want to prove that $\mpar{R', H\cup J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$. In the following we denote $H'=H\cup J_3 \setminus\{k\}$
 \begin{enumerate}
@@
 	\end{align*}
-where 
+Recall that 
 \begin{align*}
@@
 V_{23}= V_2\uplus V^2_3\\
-& H'=J_3'\uplus H \setminus \{k\} \subseteq J_3'\uplus \mpar{J_1' \cap J_2'} \setminus \{k\} = \mpar{J_3'\uplus J_1' \setminus \{k\} } \cap \mpar{J_3'\uplus J_2' \setminus \{k\}} = J_{13}'\cap J_{12}'\\
+& H' \subseteq J_3\uplus \mpar{J_1 \cap J_2} \setminus \{k\} = \mpar{J_3\uplus J_1 \setminus \{k\} } \cap \mpar{J_3\uplus J_2 \setminus \{k\}} \\
 \end{align*}
@@
 * either by the composition of a transition $t_1=\OTx{1}{}{1}{1}$ and a transition \[t_3^1=
-\OT{ s^1_3}{{s^1_3}'}{\alpha_3^1}{ \uplus  {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{ g^1_3 }{ \psi^1_3} \qquad \text{ when } k \in J'_{1} 
+\OT{ s^1_3}{{s^1_3}'}{\alpha_3^1}{   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{ g^1_3 }{ \psi^1_3} \qquad \text{ when } k \in J'_{1} 
 \]. We obtain:
@@
 \[
-\OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, {s^1_3}'}}{\alpha_1}{\beta_{1j}^{j \in J'_1 \setminus \{k\}} \uplus  {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{g_1 \wedge g^1_3 \wedge \alpha^1_3 = \beta_{1k}}{\psi_1 \uplus \psi^1_3} \qquad \text{ where } k \in J'_{1}
+t_{13} = \OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, {s^1_3}'}}{\alpha_1}{\beta_{1j}^{j \in J'_1 \setminus \{k\}} \uplus  {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{g_1 \wedge g^1_3 \wedge \alpha^1_3 = \beta_{1k}}{\psi_1 \uplus \psi^1_3} \qquad \text{ where } k \in J'_{1}
 \]
 
+We then obtain a family of OTs by the simulation of $A_1$ by $A_2$ (stated above).
+By hypothesis we have $k \in H$, so in the case where $k \in J'_{1}$, we deduce that $k \in J'_{2x}$ we can  then build  a family of OTs $t_{23x}^{x\in X}$ with the same transitions of $A_3$ (up to renaming) as those used to build $t_{13}$.
+\[
+t_{23x} = \left(\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, {s^2_3}'}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }}{g_{2x} \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2xk}}{\psi_{2x} \uplus \psi^2_3}
+\right)^{x\in X}\]
+Recall that in this case  $k \in J'_{1}$
+
 * or by an the transition $t_1=\OTx{1}{}{1}{1}$ alone with the state $s^1_3$ unchanged, if $k \not\in J_1'$
-\[\OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, s^1_3}}{\alpha_1}{\beta_{1j}^{j \in J'_1}}{g_1}{\psi_1}
+\[t_{13} = \OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, s^1_3}}{\alpha_1}{\beta_{1j}^{j \in J'_1}}{g_1}{\psi_1}
 \]
+We then obtain a family of OTs by the simulation of $A_1$ by $A_2$ (stated above).
+As  $k \in H$ we have $k \not\in J'_{2x}$ and we build:
+\[t_{23x} = \left(
+\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, s^2_3}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x}}}{g_{2x}}{\psi_{2x}} \right)^{x\in X}\]
+
 \medskip
 
-By hypothesis we have $k \in H$, so in the case where $k \in J'_{1}$, we deduce that $k \in J'_{2x}$ we can  then build  a family of OTs $t_{23x}^{x\in X}$ with the same transitions of $A_3$ (up to renaming) as those used to build $t_{13}$.
-For any $t_{23x}$  there will then be two cases according on how it is built:
-
-\[
-\choice{
-\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, {s^2_3}'}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }}{g_{2x} \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2xk}}{\psi_{2x} \uplus \psi^2_3} & \text{ if } k \in J'_{2x} \\
-\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, s^2_3}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x}}}{g_{2x}}{\psi_{2x}}& \text{otherwise}
-}
-\]
-
-So have to prove the following:
-\begin{align*}		
-		&\mpar{\forall x \in X, J'_{23x} \cap H' = J'_{13} \cap H'} \text{ and }\\
+These two cases define (depending on how $t_{13}$ is built) the family $t_{23x}$ of OTs we are looking for.
+Thus, for both cases we have to prove the following:
+\begin{align*}		
+		&\mpar{\forall x \in X, J'_{23x} \cap H' =
+ J'_{13} \cap H'} \text{ and }\\
 		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
@@
 \begin{align*}
-	\text{if } k \in J'_1:\quad &  J'_{23x} \cap H'  = 
-	\mpar{ J'_{2x}\uplus J^{2 \prime}_{3}  \setminus \mbrc{k}} \cap  \mpar{J^{2 \prime}_{3} \uplus H \setminus \mbrc{k}} \\
-		& = J^{2 \prime}_{3}  \uplus \mpar{J'_{2x} \cap H} \setminus \mbrc{k} \quad \text{ since } J^{1 \prime}_{3}=J^{2 \prime}_{3} \text{ and } J'_1 \cap H = J'_{2x} \cap H\\
-		& = J^{1 \prime}_{3} \uplus \mpar{J'_1 \cap H} \setminus \mbrc{k} \\
-		& = \mpar{ J'_1  \uplus J^{1 \prime}_{3}\setminus \mbrc{k}} \cap \mpar{J^{1 \prime}_{3} \uplus H \setminus \mbrc{k}}\\
+	\text{if } k \in J'_1:\quad &  J'_{23x} \cap H'  
+=((J'_{2x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{3} ) \cap (H\uplus J_3 \setminus\{k\} )\\
+&=((J'_{2x}\cap (H\uplus J_3))\uplus (J^{2 \prime}_{3}\cap (H\uplus J_3)))\setminus \mbrc{k}\\
+&=((J'_{2x}\cap H)\uplus (J^{2 \prime}_{3}\cap  J_3))\setminus \mbrc{k}\text{ since } J_3\cap J'_{2x} = \emptyset \text{ and } H\cap J^{2 \prime}_{3} = \emptyset\\
+& =((J'_{2x}\cap H)\uplus (J^{2 \prime}_{3}))\setminus \mbrc{k}\text{ since } J^{2 \prime}_{3}\subseteq J_3\\
+& =(J'_1\cap H)\uplus (J^{1 \prime}_{3})\setminus \mbrc{k}\quad \text{ since } J^{1 \prime}_{3}=J^{2 \prime}_{3} \text{ and } J'_1 \cap H = J'_{2x} \cap H\\
+& \text{faire reapparaitre J3 comme on l a elimine au dessus}\\
+		& = \mpar{ J'_1  \uplus J^{1 \prime}_{3}\setminus \mbrc{k}} \cap \mpar{J_{3} \uplus H \setminus \mbrc{k}}\\
 		& = J'_{13} \cap H'\\
-\text{if } k \notin J'_1:\quad &	J'_{23x} \cap H'  = \mpar{J'_{2x} \setminus \mbrc{k}} \cap \mpar{J^{2 \prime}_3 \uplus H \setminus \mbrc{k}} \\
+\text{if } k \notin J'_1:\quad &	J'_{23x} \cap H'  = \mpar{J'_{2x} } \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
+& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
+& = \mpar{J'_1\cap H }\\
+& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'\\
 \end{align*}

### 2022-01-28 2021-Refinement/paper/refinementarticle.tex
merges des diff. updates

@@
 \end{multline*}
-that can be re-written:
+
 \begin{multline*}
 %\everymath{\displaystyle}
-\forall v \in \mpar{\fvars{\alpha_{1}}  \cup \bigcup_{j \in J'_{2px} \cap H} \!\fvars{\beta_{1j}}} \setminus \mpar{V_1 \uplus V_2 \uplus \fvars{t_1}}, \\ \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X_p} \mpar{\everymath{\displaystyle}
+\bigforall V_1 \uplus V_2 \uplus \fvars{t_1}\,\,
+\bigexists \mpar{\fvars{\alpha_{1}}  \cup
+\!\!\!
+\bigcup_{j \in J'_{2px} \cap H}\!\!\!\!\!\fvars{\beta_{1j}}} \setminus \mpar{V_1 \uplus V_2 \uplus \fvars{t_1}}, \\ \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X_p} \mpar{\everymath{\displaystyle}
 \begin{array}{l}
@@
 			 g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}} \land R_{23}\mpar{s_{2p},s_3}
-		\end{array}} \\
+		\end{array}} \qquad (*) \\
 \end{align*}
@@
 \end{multline*}
-that can be re-written:
+that can be re-written as follows:
 \begin{multline*}
 \everymath{\displaystyle}
-\forall v\in \mpar{\fvars{\alpha_{2px}}  \cup \bigcup_{j \in J'_{3pxy}
-\cap H'} \!\!\fvars{\beta_{2pxj}}} \setminus \mpar{V_2 \uplus V_3 \uplus \fvars{t_{2px}}},\\ \mpar{R_{23}\mpar{s_{2p}, s_{3}} \wedge g_{2px} \implies \operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
+\bigforall V_2 \uplus V_3 \uplus \fvars{t_{2px}}\,\,\bigexists \mpar{\fvars{\alpha_{2px}} \cup\!\!\!\!\!\! \bigcup_{j \in J'_{3pxy}
+\cap H'}\!\!
+\!\!\!\!\fvars{\beta_{2pxj}}} \setminus \mpar{V_2 \uplus V_3 \uplus \fvars{t_{2px}}},\\ \mpar{R_{23}\mpar{s_{2p}, s_{3}} \wedge g_{2px} \implies \operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
 \begin{array}{l}
@@
 			 g_{3pxy} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
-		\end{array}}} 
+		\end{array}}} \qquad (**)
 \end{multline*}
@@
 $\forall x \in X, \forall y \in Y,  J'_1 \cap (H \cap H') = J'_{3pxy} \cap (H\cap H')$ \\
-In addition, we get: \\
-$\displaystyle {\forall v \in \mpar{\fvars{\alpha_{1}}  \cup \bigcup_{j \in J'_{2px} \cap H} \!\fvars{\beta_{1j}}  \cup \fvars{\alpha_{2px}}  \cup \bigcup_{j \in J'_{3pxy} \cap H'} \!\fvars{\beta_{2pxj}}} } \setminus \\ \mpar{V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1}\uplus \fvars{t_{2px}}}
-$
-\begin{align*}
+In addition, by replacing the formula $(**)$ in $(*)$, we get: 
+\begin{multline*}
+\everymath{\displaystyle}
+\bigforall V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1}\uplus \fvars{t_{2px}}\\ 
+\bigexists  \mpar{\fvars{\alpha_{1}}  \cup \!\!\!\!\!\!\bigcup_{j \in J'_{2px} \cap H} \!\!\!\!\!\!\!\fvars{\beta_{1j}}  \cup \fvars{\alpha_{2px}}  \cup \!\!\!\!\!\!\bigcup_{j \in J'_{3pxy} \cap H'} \!\!\!\!\!\!\!\fvars{\beta_{2pxj}}}  \setminus \\ \mpar{V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1}\uplus \fvars{t_{2px}}}  \\
 R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies \hspace{4.5cm}\\\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
@@
 		\end{array}} 
-\end{align*}		
-With the restriction of the domain and the simplification of the formula, we get:\\
-$\displaystyle {\forall v \in \mpar{\fvars{\alpha_{1}}  \cup\!\!\!
-\!\!\bigcup_{j \in J'_{3pxy} \cap H \cap H'} \!\!\!\!\!\fvars{\beta_{1j}}  \cup \fvars{\alpha_{2px}}  \cup\!\!\!
-\!\!\bigcup_{j \in J'_{3pxy} \cap H\cap H'} \!\!\!\!\!\fvars{\beta_{2pxj}}} } \setminus \\ \mpar{V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1}\uplus \fvars{t_{2px}}}
-$
-\begin{align*}
+\end{multline*}		
+With the restriction of the domain and the rearrangement of the formula, we get:
+\begin{multline*}
+\everymath{\displaystyle}
+\bigforall V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1}\uplus \fvars{t_{2px}}\\ \bigexists  \mpar{\fvars{\alpha_{1}}  \cup \!\!\!\!\!\!\bigcup_{j \in J'_{3pxy} \cap (H\cap H')} \!\!\!\!\!\!\!\fvars{\beta_{1j}}  \cup \fvars{\alpha_{2px}}  \cup \!\!\!\!\!\!\bigcup_{j \in J'_{3pxy} \cap (H\cap H')} \!\!\!\!\!\!\!\fvars{\beta_{2pxj}}}  \setminus \hspace{6cm}\\ \mpar{V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1}\uplus \fvars{t_{2px}}}  \\
 R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies 
@@
 \end{array}}
-\end{align*}
+\end{multline*}
 
@@
 \alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap (H\cap H')} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
-R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}
+\mpar{R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}
 \end{array}}
@@
 \begin{multline*}
+\everymath{\displaystyle}
+\bigforall V_1 \uplus  V_3 \uplus \fvars{t_1}\\
+\bigexists \mpar{\fvars{\alpha_{1}}  \cup\!\!\! \bigcup_{j \in J'_{3z} \cap H \cap H'} \!\!\!\fvars{\beta_{1j} } } \setminus  \mpar{V_1 \uplus  V_3 \uplus \fvars{t_1}}\hspace{3cm}\\
 R_{13}(s_1,s_3)  \wedge g_1 \implies 
@@
 \begin{array}{l}
-\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap (H\cap H')} \beta_{1j}=\beta_{3jpxy} \wedge\\ g_{3pxy} 
+\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap (H\cap H')} \beta_{1j}=\beta_{3jpxy} \\ \wedge g_{3pxy} 
 {\wedge R_{13}\mpar{s'_1,s'_{3pxy}}}\psubst{\psi_1  \uplus \psi_{3pxy}}
@@
 All  combinations of elements in $P$, $X$, and $Y$ provide a set $Z$ of weak open transitions.
-This allows us to get the desired conclusion, that there is a set of weak open transitions indexed over $Z$:\\
+This allows us to get the desired conclusion, that there is a set of weak open transitions indexed over $Z$:
 %This provides the desired conclusion:\\
-$\forall z \in Z,  J'_1 \cap (H \cap H') = J'_{3z} \cap (H\cap H')$\\
-$\displaystyle {\forall v \in \mpar{\fvars{\alpha_{1}}  \cup\!\!\! \bigcup_{j \in J'_{3z} \cap H \cap H'} \!\!\!\fvars{\beta_{1j} } } \setminus  \mpar{V_1 \uplus  V_3 \uplus \fvars{t_1}}},$
-\begin{align*}
+\begin{multline*}
+V_1 \uplus  V_3 \uplus \fvars{t_1}
+\vdash\\\hspace{2em}
 \mpar{R_{13}\mpar{s_1, s_3} \wedge g_1 \implies 
@@
 \end{array}}}
-\end{align*}	
+\end{multline*}	
 \medskip
@@
 \everymath{\displaystyle}
-\forall v\in \mpar{\fvars{\alpha_{3}}  \cup \!\!\bigcup_{j \in J'_{3}} \!\!\fvars{\beta_{3j}}} \cup \mpar{\fvars{\alpha_{2px}}  \cup \!\!\! \bigcup_{j \in J'_{2p}} \!\!\!\fvars{\beta_{2pxj}}}
+\bigforall \mpar{V_2\! \uplus\!V_3 \uplus\!\! \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3}}\\
+\bigexists \mpar{\fvars{\alpha_{3}}  \cup \!\!\bigcup_{j \in J'_{3}} \!\!\fvars{\beta_{3j}}} \cup \mpar{\fvars{\alpha_{2px}}  \cup \!\!\! \bigcup_{j \in J'_{2p}} \!\!\!\fvars{\beta_{2pxj}}}
  \setminus \mpar{V_2\! \uplus\!V_3 \uplus\!\! \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3}},\\
@@
 \everymath{\displaystyle}
-\forall v\in \mpar{\fvars{\alpha_{2px}}  \cup  \bigcup_{\begin{array}{c} \subbox{p\in P}\\ \subbox{j \in J'_{2p}}
+\bigforall \mpar{V_1\! \uplus\! V_2\! \uplus  \biguplus_\subbox{t_{2p} \in \fOT{s_{2p}}} \fvars{t_{2p}}}\\
+\bigexists \mpar{\fvars{\alpha_{2px}}  \cup  \bigcup_{\begin{array}{c} \subbox{p\in P}\\ \subbox{j \in J'_{2p}}
 \end{array}} \!\! \fvars{\beta_{2pxj}}}\cup \mpar{\fvars{\alpha_{1}}  \cup\!\! \bigcup_{j \in J'_{1}} \!\!\fvars{\beta_{1j}}}
- \setminus \mpar{V_1\! \uplus\! V_2\!\! \uplus \biguplus_\subbox{t_{2p} \in \fOT{s_{2p}}} \fvars{t_{2p}}},\\
+ \setminus \mpar{V_1\! \uplus\! V_2\! \uplus \biguplus_\subbox{t_{2p} \in \fOT{s_{2p}}} \fvars{t_{2p}}},\\
 R_{12}\mpar{s_1, s_{2p}} \wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
@@
 \everymath{\displaystyle}
-\forall v\in \mpar{\fvars{\alpha_{3}}  \cup \!\!\bigcup_{j \in J'_{3}} \!\!\fvars{\beta_{3j}}} \cup \mpar{\fvars{\alpha_{1}}  \cup\!\! \bigcup_{j \in J'_{1}} \!\!\fvars{\beta_{1j}}}
+\bigforall \mpar{V_1\! \uplus\!V_3 \uplus\!\! \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3}}\\
+\bigexists \mpar{\fvars{\alpha_{3}}  \cup \!\!\bigcup_{j \in J'_{3}} \!\!\fvars{\beta_{3j}}} \cup \mpar{\fvars{\alpha_{1}}  \cup\!\! \bigcup_{j \in J'_{1}} \!\!\fvars{\beta_{1j}}}
  \setminus \mpar{V_1\! \uplus\!V_3 \uplus\!\! \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3}},\\
@@
 
-From the formula $(*)$ to which we have added the same terms ($g_3 \wedge \alpha_3=\beta_{1k} {\displaystyle \wedge\bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3}$) to both sides of the implication and from all the points mentioned above, we get:\\
-
-$\displaystyle {\forall v \in \mpar{\fvars{\alpha_{13}}  \cup\!\!\!
-\bigcup_{j \in J'_{23x}} \!\!\!\fvars{\beta_{13j} } } \setminus  \mpar{V_1 \uplus  V_2  \uplus V_3 \uplus  \fvars{t_1} \uplus \fvars{t_3}}},$
-\begin{multline*}
+From the formula $(*)$ to which we have added the same terms ($g_3 \wedge \alpha_3=\beta_{1k} {\displaystyle \wedge\bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3}$) to both sides of the implication and from all the points mentioned above, we get:
+\begin{multline*}
+\bigforall V_1 \uplus  V_2  \uplus V_3 \uplus  \fvars{t_1} \uplus \fvars{t_3}\\
+\bigexists \mpar{\fvars{\alpha_{13}}  \cup\!\!\! \bigcup_{j \in J'_{23x}} \!\!\!\fvars{\beta_{13j} } } \setminus  \mpar{V_1 \uplus  V_2  \uplus V_3 \uplus  \fvars{t_1} \uplus \fvars{t_3}}\\
 R\mpar{s_1, s_{2}} \wedge g_1 \wedge g_3 \wedge \alpha_3=\beta_{1k} \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3\implies\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}

### 2022-02-02 2021-Refinement/paper/refinementarticle.tex
corrections debut preuve thm2

@@
 \section{Proof of Context Refinement}
+
+\proof
 Let us denote by $A_{13}$ (resp.
@@
 Let $R$ be the refinement relation relating states of $A_1$ and $A_2$. 
-Let us consider any two states $s_{13} = \mpar{s_1,s^1_3}$ and $s_{23} = \mpar{s_2,s^2_3}$ ($s^1_3$ and $s^2_3$  are the same with renaming).
-We define a relation $R'$ relating states of $A_{13}$ and $A_{23}$ as follows:
+Let us denote with $t^1$ and $t^2$  the elements of $A_1$ and $A_2$ respectively.
+Consider any two states $s_{13} = \mpar{s_1,s^1_3}$ and $s_{23} = \mpar{s_2,s^2_3}$ ($s^1_3$ and $s^2_3$  are the same with renaming).
+We define a relation $R'$ relating states of $s_{13}$ and $s_{23}$ as follows:
 \[ R' \mpar{s_{13}, s_{23}} = R\mpar{s_{1}, s_{2}} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigwedge_\subbox{v_3\in \fvars{s_{3}}
@@
 \begin{enumerate}
-\item First, we have to prove:
+\item First, we have to prove the following:
 \[\sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}\]
-
-By using the fact that $R$ relates initial configurations of  $A_1$ and $A_2$, we have  the following statement holds:
-$\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}}$.
-And secondly, because the domain of the substitution function is disjoint from the others, it has an effect only on the related elements, and relying on the  fact that initial states are reachable we  have:\TODO{define states and assignments}
+with $\sigma_{013} = \sigma_{01} \uplus \sigma_{03}^1$ and $\sigma_{023} = \sigma_{02} \uplus \sigma_{03}^2$.\\
+By using the fact that $R$ relates initial configurations of  $A_1$ and $A_2$, we have  the following statement:
+$\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}}$,  and relying on the  fact that initial states are reachable $\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ we have 
+\[ \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
+\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\]
+Composing with a tautology ${\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}$  and considering that  the domains of the substitution function are disjoint, the substitution function has an effect only on the related elements,  we get:
 \begin{align*}
@@
 \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
-\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \wedge\underbrace{  \bigwedge_\subbox{v_3\in V_3} \sigma^1_{03}(v^1_3)=\sigma^2_{03}(v^2_3)\wedge s^1_3 = s^2_3}_{\Longleftrightarrow~\top?????}\\
+\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}}  \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3\\
 \implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma_{013} \uplus \sigma^1_{03}\uplus \sigma^2_{03} }\\
@@
 &=((J'_{2x}\cap H)\uplus (J^{2 \prime}_{3}\cap  J_3))\setminus \mbrc{k}\text{ since } J_3\cap J'_{2x} = \emptyset \text{ and } H\cap J^{2 \prime}_{3} = \emptyset\\
-& =((J'_{2x}\cap H)\uplus (J^{2 \prime}_{3}))\setminus \mbrc{k}\text{ since } J^{2 \prime}_{3}\subseteq J_3\\
-& =(J'_1\cap H)\uplus (J^{1 \prime}_{3})\setminus \mbrc{k}\quad \text{ since } J^{1 \prime}_{3}=J^{2 \prime}_{3} \text{ and } J'_1 \cap H = J'_{2x} \cap H\\
-& \text{faire reapparaitre J3 comme on l a elimine au dessus}\\
-		& = \mpar{ J'_1  \uplus J^{1 \prime}_{3}\setminus \mbrc{k}} \cap \mpar{J_{3} \uplus H \setminus \mbrc{k}}\\
+& =((J'_{2x}\cap H)\uplus J^{2 \prime}_{3})\setminus \mbrc{k}\text{ since } J^{2 \prime}_{3}\subseteq J_3\\
+& =(J'_1\cap H)\uplus J^{1 \prime}_{3}\setminus \mbrc{k}\quad \text{ since } J^{1 \prime}_{3}=J^{2 \prime}_{3} \text{ and } J'_1 \cap H = J'_{2x} \cap H\\
+&= ((J'_1 \cap H) \uplus (J^{1 \prime}_{3} \cap J_3)) \setminus \mbrc{k}\text{ since } J^{1 \prime}_{3}\subseteq J_3\\ 
+& = (J'_1\cap (J_3 \uplus H)) \uplus ((J^{1 \prime}_{3} \cap (J_3 \uplus H)) \setminus \mbrc{k} \text{ since } J_3\cap J'_{1} = \emptyset \text{ and } H\cap J^{1 \prime}_{3} = \emptyset\\
+		& = \mpar{(J'_1  \uplus J^{1 \prime}_{3})\setminus \mbrc{k}} \cap \mpar{(J_{3} \uplus H) \setminus \mbrc{k}}\\
 		& = J'_{13} \cap H'\\

### 2022-02-03 2021-Refinement/paper/refinementarticle.tex
work on proof and minor things

@@
 
-- reflexivity and transitivity
-
-We will  show  that  the  refinement  is  reflexive  and  transitive,  so  it  is  a  preorder on the set of open automata.
-
-\begin{lemma} The relation \(\wrel{}{}{H}\) is a preorder thus enables stepwise refinement.
-\end{lemma}
-The relation  \(\wrel{}{}{H}\) is reflexive,  \(\wrel{A}{A}{H}\),  by taking $R\mpar{s_1, s_2} \mapsto \displaystyle\bigwedge_\subbox{v \in vars(s_1)} {v=v}$ to be $s_1= s_2$  and checking the above conditions (Definition \ref{Def:OA-Refinement}), we can see that \TODO{finish the sentence}\\
+The first crucial property of  refinement  is that it is reflexive  and  transitive,  so  it  is  a  preorder on the set of open automata. This property enables stepwise refinement.
+
+The relation  \(\wrel{}{}{H}\) is reflexive,  \(\wrel{A}{A}{H}\),  by taking $R\mpar{s_1, s_2} \mapsto \displaystyle\bigwedge_\subbox{v \in vars(s_1)} {v=v}$ to be $s_1= s_2$  and checking the above conditions (Definition \ref{Def:OA-Refinement}), we can see that the relation is indeed reflexive.
 
@@
 
+We denote $A_1=  \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}$ and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and $A_3 = \OA{S_3}{s_{03}}{J_3}{V_3}{\sigma_{03}}{T_3}$
+
 Let $R$ be the refinement relation relating states of $A_1$ and $A_2$. 
@@
 \[\sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}\]
-with $\sigma_{013} = \sigma_{01} \uplus \sigma_{03}^1$ and $\sigma_{023} = \sigma_{02} \uplus \sigma_{03}^2$.\\
+with $\sigma_{013} = \sigma_{01} \uplus \sigma_{03}^1$, $\sigma_{023} = \sigma_{02} \uplus \sigma_{03}^2$, $s_{013}=(s_{01},s_{03}^1)$, and $s_{023}=(s_{02},s_{02}^2)$.\\
 By using the fact that $R$ relates initial configurations of  $A_1$ and $A_2$, we have  the following statement:
@@
 \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\]
-Composing with a tautology ${\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}$  and considering that  the domains of the substitution function are disjoint, the substitution function has an effect only on the related elements,  we get:
+
+Considering that initial valuations $\sigma_{03}^1$ and $\sigma_{03}^2$ associate the same values to the ``same'' variables modulo renaming, we have the tautology:\\ $\left({\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }$.
+
+Because  the domains of the substitution function are disjoint, the substitution function has an effect only on the related elements,  we get:
 \begin{align*}
@@
 \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
-\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}}  \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3\\
-\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma_{013} \uplus \sigma^1_{03}\uplus \sigma^2_{03} }\\
+\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3\\
+\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma^1_{03}\uplus \sigma^2_{03} }\\
 \implies & \sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}
@@
 
+\TODO{the subtelty here is that the original relation implies that valuations in A3 are equal (ie the value for each variable are the same in both valuations, modulo renaming), after a transition we should obtain ``equal'' valuations because Post are deterministic}
+
 From the formula $(*)$ to which we have added the same terms ($g_3 \wedge \alpha_3=\beta_{1k} {\displaystyle \wedge\bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3}$) to both sides of the implication and from all the points mentioned above, we get:

### 2022-02-03 2021-Refinement/paper/refinementarticle.tex
writing up in readlock reduction and non-blocking composition

@@
 By relation on these invariants they introduce several refinement relations.
-We could have done something similar for non-locking composition reachability predicates which are introduced in Section \ref{sec:proofelts}.
+We could have done something similar for non-blocking composition reachability predicates which are introduced in Section \ref{sec:proofelts}.
 
@@
 
-\TODO{commmenter avec}
-
-perhaps say that one of the automaton is expected to be the refinement of the other BUT the def is not dependent on the notion of refinement
-
-Beware implicit existential quantification on vars of t1
-
-Next definition is not intuitive, it does not say much because it says that if t2 is not in a deadlock position then t1 can do a transition but not necessarily with the same input values.
+A notion that is often used in the context of refinement is the notion of deadlock reduction.
+This property considers that two states related by a given relation and states that if one state can do a transition, then the other can do a transition too.
+This notion is not much interesting in the general case as there is a priori no relation between the two transitions.
+However, when the relation that relates states is a simulation, this will relate the possible transitions and the deadlock reduction will become a valuable property.
+
+Next definition states that if $T_2$ is not in a deadlock position then $T_1$ can do a transition but not necessarily with the same input values.
 This is very weak but sufficient when composed with the def  of simulation.
@@
 Let \(\OAg[1]\) and \(\OAg[2]\) be two OAs.
-A relation on OA configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if  it satisfies the following:
+A relation on OA configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if  it satisfies the following\footnote{Note that variables of $T_1$ are existentially quantified in the proposition.}:
 \begin{multline*}
@@
 
-One important aspect to notice is that in this definition, because of the symbolic nature of OAs and their structure, the fact that a guard is true is sufficient to reason on the possible paths.
-This slightly simplifies the definition and makes the characterisation of transition that can be triggered more symbolic.
-An equivalent  definition of deadlock reduction can be expressed: it states that if there is a transition that can be triggered in the first automaton, then there is a transition from the related state in the second automaton that can be triggered.
-This second definition is more complex, in particular because of the multiple quantifiers over transitions and automaton state.
+Because of the symbolic nature of OAs and their structure, in this definition,  the fact that a guard is true is sufficient to reason on the possible paths.
+This slightly simplifies the definition and makes the characterisation of transition that can be triggered very symbolic.
+An equivalent but more classical definition of deadlock reduction could be expressed as well.
+It states that if there is a transition that can be triggered in the first automaton, then there is a transition from the related state in the second automaton that can be triggered.
+This second definition is more verbose, in particular because of the multiple quantifiers over transitions and automaton state.
 The alternative definition is equivalent to this one when reasoning on a refinement relation (but not in general).
 
-Unfortunately, in the general case, this property is not much useful in general because it conflicts with the possibility to compose automata: The composition operator can itself introduce a deadlock.
-A way to solve the conflict between deadlock reduction and the properties involving composition is to only consider a composition that do not introduce deadlocks.
-
-Before characterising a composition which does not introduce deadlocks we need to be able to tell which states are reachable.
+Unfortunately, this property is not compositional: the composition operator can itself introduce a deadlock.
+In other words, when filling the hole of two related automata with a third one, even if there is a deadlock reduction between the two original automata , there might not be a deadlock reduction in the composed ones.
+The same problem may arise when two related automata are composed in the same hole of a third one.
+
+This creates a conflict between deadlock reduction and the properties involving composition.
+One possible solution to avoid this conflict is to only consider a composition that do not introduce deadlocks, we will define such a composition below.
+But before defining non-blocking composition, we first introduce a notion of state reachability for open automata. 
 \begin{definition}[Reachability] \label{Def:Reach}
@@
 Reachability takes into account all paths, and can over-approximate the reachable configurations. 
-\TODO{rediger la phrase suivante}
-Because of the over approximation, to implement a verifier it is possible to try find a formula that over-approximate the reachability property and is representable in the tool.
-% LUDO HERE
-\begin{definition}[Non-locking composition]
+From an automation point of view, finding the most precise reachability predicate for a given automata is not decidable because of the symbolic nature of open automata, but only an over-approximation is necessary.
+An automatic tool would only need to find an over approximation of reachability to reason on composition that is compatible with deadlock reduction.
+We call \emph{non-blocking composition} a composition that can be safely be used to compose open automata that are involved in a deadlock reducing relation.
+
+\begin{definition}[Non-blocking composition]
 Let \(A_i = \OAg[i]\) with \( 0 \leq i \leq n\) be a family of open automata.
@@
 
-The composition \(A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is non-locking if   \(A \) has a reachability predicate such that, for each reachable configuration, if there is a possible transition in \(A_0\) then there is a possible transition in \(A\):
+The composition \(A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is non-blocking if   \(A \) has a reachability predicate such that, for each reachable configuration, if there is a possible transition in \(A_0\) then there is a possible transition in \(A\):
 \[ \forall s = \mpar{s_0, s_1,..,s_n} \in S, V \uplus \biguplus_\subbox{t_0 \in \fOT{s_0}} \fvars{t_0} \vdash \left(\reach{A}\mpar{s} \wedge \bigvee_\subbox{t_0 \in \fOT{s_0}} \fguard{t_0} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \right)\]
@@
 Let $J_3$ be the set of holes of $A_3$.
-Suppose that \(k \in H\) and that \(A_1\subst{A_3}{k}\) is non-locking.
+Suppose that \(k \in H\) and that \(A_1\subst{A_3}{k}\) is non-blocking.
 We have: \[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{J_3 \uplus H \setminus \mbrc{k}}\].
@@
 Let $A_1$, $A_2$ and $A_3$ be three open automata with $\wrel{A_2}{A_3}{H}$. 
-Suppose that \(k \in H\) and that \(A_1\subst{A_2}{k}\) is non-locking.
+Suppose that \(k \in H\) and that \(A_1\subst{A_2}{k}\) is non-blocking.
 We have: \[\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{J_1 \uplus H \setminus \mbrc{k}}\].
 \end{theorem}
-- composition is a refinement (under which condition? non-locking composition?)
+- composition is a refinement (under which condition? non-blocking composition?)
 
@@
 
-\TODO{the subtelty here is that the original relation implies that valuations in A3 are equal (ie the value for each variable are the same in both valuations, modulo renaming), after a transition we should obtain ``equal'' valuations because Post are deterministic}
+\TODO{The subtlety here is that the original relation implies that valuations in A3 are equal (ie the value for each variable are the same in both valuations, modulo renaming), after a transition we should obtain ``equal'' valuations because Post are deterministic}
 
@@
 \end{multline*}
-By hypothesis we also have \(A_1\subst{A_3}{k}\) is non-locking,  thus we can write the following:
+By hypothesis we also have \(A_1\subst{A_3}{k}\) is non-blocking,  thus we can write the following:
 \[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	

### 2022-02-09 2021-Refinement/paper/refinementarticle.tex
encore un pas preuve...

@@
 		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
-			\nwedge g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \wedge\\[12pt]
+			 g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
 		\end{array}} 
@@
 \end{align*}
-
 For the rest of the formula we will also consider the two cases separately. 
-
 \begin{itemize}
-\item If $k \in J'_1$: we will extend the valuation context of the variables to cover the variables of the transition $t_3$.
-Based on this fact we have: $ \alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$ because composition doesn't change the resulting actions, nor their variables.
-We also have 
-${\displaystyle \bigwedge_\subbox{j \in J'_{23x} \cap H} \beta_{1j} = \beta_{2xj} \Rightarrow  \bigwedge_\subbox{j \in J'_{23x} \cap H} \beta_{13j} = \beta_{23xj}}$ since the actions of the holes in $J_3$ coincide on both sides.
-And the following statements:
-$g_{13} \Leftrightarrow g_1 \wedge g_3 \wedge \alpha_3=\beta_{1k}$, 
-$g_{23x}  \Leftrightarrow g_{2x} \wedge g_3 \wedge \alpha_3=\beta_{2xk}$ and $\beta_{1k} = \beta_{2xk}$\\
+\item if $k \in J'_1$:\\
+Because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$, we will then have:\\ $ \alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$ and
+${\displaystyle \bigwedge_\subbox{j \in J'_{23x} \cap H} \beta_{1j} = \beta_{2xj} \Rightarrow  \bigwedge_\subbox{j \in (J'_{2x} \cap H)\uplus J_3} \beta_{13j} = \beta_{23xj}}$\\
+On another side,   the composition gives $g_{13} \Leftrightarrow g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}$ and
+$g_{23x}  \Leftrightarrow g_{2x} \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk}$. \\
+In addition $k \in H$ we have   
+$\beta_{1k} = \beta_{2xk}$ then we  deduce:
+$g^1_3 \wedge \alpha^1_3=\beta_{1k}  \Leftrightarrow g^2_3 \wedge \alpha^2_3= \beta_{2xk}$
 
@@
 
-From the formula $(*)$ to which we have added the same terms ($g_3 \wedge \alpha_3=\beta_{1k} {\displaystyle \wedge\bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3}$) to both sides of the implication and from all the points mentioned above, we get:
-\begin{multline*}
-\bigforall V_1 \uplus  V_2  \uplus V_3 \uplus  \fvars{t_1} \uplus \fvars{t_3}\\
-\bigexists \mpar{\fvars{\alpha_{13}}  \cup\!\!\! \bigcup_{j \in J'_{23x}} \!\!\!\fvars{\beta_{13j} } } \setminus  \mpar{V_1 \uplus  V_2  \uplus V_3 \uplus  \fvars{t_1} \uplus \fvars{t_3}}\\
-R\mpar{s_1, s_{2}} \wedge g_1 \wedge g_3 \wedge \alpha_3=\beta_{1k} \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3\implies\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{13j} = \beta_{23xj} \nwedge\\
-			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}}  \wedge g_3 \wedge \alpha_3=\beta_{2xk} \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s'^1_3=s'^2_3
+By adding the same (and equivalent) terms  to both sides of the implication of the formula $(*)$,  and  from all the implications induced by the extension of the valuation context mentioned above, we get:
+\begin{multline*}
+V_1 \uplus V_2 \uplus \fvars{t_1} \uplus V^1_3  \uplus V^2_3 \vdash\\
+R\mpar{s_1, s_{2}} \wedge g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k} %\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
+\implies  \hspace{12em}\\
+\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in (J'_{2x} \cap H)\uplus J_3} \beta_{13j}\! =\! \beta_{23xj}\\
+			 \nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}}  \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk} 
+%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
 \end{multline*}	
@@
 \begin{multline*}
-R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3\implies\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{13j} = \beta_{23xj} \nwedge\\
-			 g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s'^1_3=s'^2_3
+V_{13} \uplus V_{23} \uplus \fvars{t_1}  \vdash\\
+R\mpar{s_1, s_{2}} \wedge g_{13}  
+%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
+\implies  \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\
+			\nwedge g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
 		\end{array}}   
@@
 
-By hypothesis $\reach{A_{13}}\mpar{s_{13}}$ holds,  we then have according to the Definition \ref{Def:Reach} the following:
+By hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
 \[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
+From these two previous formulas we obtain:
+\begin{multline*}
+V_{13} \uplus V_{23} \uplus \fvars{t_1}  \uplus \fvars{t_{13}} \vdash\\
+R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \reach{A_{13}}\mpar{s_{13}}
+%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
+\implies  \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\
+			\nwedge g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} 
+%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
+		\end{array}}   \wedge \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
+\end{multline*}
+
+Considering that ate each step the valuations $\sigma_{3}^1$ and $\sigma_{3}^2$ associate the same values to the ``same'' variables modulo renaming, we have the tautology:\\ $\left({\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{3}^1 \uplus \sigma_{3}^2 }$.
+
 \end{itemize}
@@
 
- that gives,  according to Definition \ref{Def:CompOA}
-
-The open transition $t_{13}$ is obtained by the composition of $t_1=\OTx{1}{}{1}{1}$ and $t_3=\OTx{3^1}{}{3}{3}$, that gives,  according to Definition \ref{Def:CompOA}, an open transition in one of the following forms:
-% \[  \choice{
-%	\OTx{1}{}{1}{1} \text{ and }  \OTx{3}{}{3}{3}
-%	& \text{if } k \in J'_{1} \\
-%	\OTx{1}{}{1}{1}	 & \text{otherwise}
-%	} \]
-\[
-\choice{
-\OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, {s^1_3}'}}{\alpha_1}{\beta_j^{j \in J'_1 \uplus J'_3 \setminus \{k\}}}{g_1 \wedge g_3 \wedge \alpha_3 = \beta_{1k}}{\psi_1 \uplus \psi_3} & \text{ if } k \in J'_{1} \\
-\OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, s^1_3}}{\alpha_1}{\beta_j^{j \in J'_1}}{g_1}{\psi_1}& \text{otherwise}
-}
-\]
-
-We have  $k \in H$ and $k \in J'_{1}$ then  we have $k \in J'_{2x}$.\\
-By composing the family of OTs  $t_{2x}^{x\in X}$ originating from  $s_2$ with an open transition $t_3=\OTx{3}{}{3}{3} \in T_3$
-%$t_3 =\OT{q_3}{q_3'}{\alpha_{3}'}{\beta_j^{j \in J''_{3}}}{g_{3}'}{\psi_{3}'} \in T_3$ %${\OT{q_{3}}{q'_{3}}{\alpha_{3}}{\beta_{ j}^{j \in J'_{3}}}{g_{3}}{\psi_{3}}}$, 
-gives a family of OTs $t_{23x}^{x\in X}$.  The result of the composition will be as follows:
-\begin{enumerate}
-\item if $ s^1_3=s^2_3$
-\[
-\choice{
-\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, {s^2_3}'}}{\alpha_{2x}}{\beta_j^{j \in J'_{2x} \uplus J'_3 \setminus \{k\}}}{g_{2x} \wedge g_3 \wedge \alpha_3 = \beta_{2xk}}{\psi_{2x} \uplus \psi_3} & \text{ if } k \in J'_{2x} \\
-\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, s^2_3}}{\alpha_{2x}}{\beta_j^{j \in J'_{2x}}}{g_{2x}}{\psi_{2x}}& \text{otherwise}
-}
-\]
-\item if $s^1_3 \neq s^2_3$ no element is produced that results an empty family.
-\end{enumerate}
-
-It remains to prove that we have:
-\begin{align*}		
-		&\mpar{\forall x \in X, J'_{23x} \cap H' = J'_{13} \cap H'} \text{ and }\\
-		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
-			\nwedge g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
-		\end{array}} 
-	\end{align*}
-
-For all $x \in X$ we have two cases:
-\begin{align*}
-		\text{if } k \in J'_1: && J'_{23x} \cap H' & = \mpar{J'_{3} \uplus J'_{2x} \setminus \mbrc{k}} \cap  \mpar{J'_{3} \uplus H \setminus \mbrc{k}}\\
-		&&& = J'_{3}  \uplus \mpar{J'_{2x} \cap H} \setminus \mbrc{k} \\
-		&&& = J'_{3} \uplus \mpar{J'_1 \cap H} \setminus \mbrc{k} \\
-		&&& = \mpar{ J'_{3} \uplus J'_1 \setminus \mbrc{k}} \cap \mpar{J'_{3} \uplus H \setminus \mbrc{k}}\\
-		&&& = J'_{13} \cap H'\\
-\text{if } k \notin J'_1: && J'_{23x} \cap H' & = \mpar{J'_{2x} \setminus \mbrc{k}} \cap \mpar{J'_3 \uplus H \setminus \mbrc{k}} \\
-		&&& = \mpar{J'_{2x} \cap H} \setminus \mbrc{k} \\
-		&&& = \mpar{J'_1 \cap H} \setminus \mbrc{k}  \\
-		&&& = J'_3 \uplus \mpar{J'_1 \cap H} \setminus \mbrc{k}  \\
-		&&& = J'_{13} \cap H'
-		\end{align*}
-
-\smallskip
-
-By adding the same terms to both sides of the implication of the  formula $(*)$, we get:
-
-\begin{itemize}
-\item In the case $ s^1_3=s^2_3$ and $k \in J'_1$:\\
-$\displaystyle {\forall v \in \mpar{\fvars{\alpha_{1}}  \cup\!\!\! \bigcup_{j \in J'_{2x}} \!\!\!\fvars{\beta_{1j} } } \setminus  \mpar{V_1 \uplus  V_2 \uplus \fvars{t_1}}},$
-\begin{multline*}
-R\mpar{s_1, s_{2}} \wedge g_1 \wedge g_3 \wedge \alpha_3=\beta_{1k} \wedge s^1_3=s^2_3\implies\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \nwedge\\
-			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}}  \wedge g_3 \wedge \alpha_3=\beta_{1k} \wedge s^1_3=s^2_3
-\end{multline*}	
-Based on the fact that the composition doesn't change the resulting actions, nor the variables, and on the fact that for $k \in H$ we have $\beta_{1k}=\beta_{2xk}$, the we get after simplification:
-\begin{multline*}
-R\mpar{s_1, s_{2}} \wedge g_{13} \wedge s^1_3=s^2_3\implies\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H} \beta_{1j} = \beta_{2xj} \nwedge\\
-			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}}  \wedge g_3 \wedge \alpha_3=\beta_{1k} \wedge s^1_3=s^2_3
-\end{multline*}
-
-By hypothesis $\reach{A_{13}}\mpar{s_{13}}$ holds,  we then have according to the Definition \ref{Def:Reach} the following:
-\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
-\end{itemize}
 \TODO{Pas termine: valider d'abord la definition de R}

### 2022-02-10 2021-Refinement/paper/refinementarticle.tex
samll changes ...

@@
 
-We want to prove that $\mpar{R', H\cup J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$. In the following we denote $H'=H\cup J_3 \setminus\{k\}$
+We want to prove that $\mpar{R', H\uplus J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$. In the following we denote $H'=H\cup J_3 \setminus\{k\}$
 \begin{enumerate}
@@
 
-Considering that initial valuations $\sigma_{03}^1$ and $\sigma_{03}^2$ associate the same values to the ``same'' variables modulo renaming, we have the tautology:\\ $\left({\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }$.
+Considering that initial valuations $\sigma_{03}^1$ and $\sigma_{03}^2$ associate the same values to the ``same'' variables modulo renaming, we have the tautology:\\ $\left(\,\,\,\,{\displaystyle \bigwedge_\subbox{v_3\in vars(s_3)} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }$.
 
@@
 \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
-\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3\\
-\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma^1_{03}\uplus \sigma^2_{03} }\\
+\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \land \bigwedge_\subbox{v_3\in vars(s_3)} v^1_3=v^2_3\wedge s^1_3 = s^2_3\\
+\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v_3\in vars(s_3)}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma^1_{03}\uplus \sigma^2_{03} }\\
 \implies & \sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}
@@
 \item if $k \in J'_1$:\\
-Because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$, we will then have:\\ $ \alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$ and
-${\displaystyle \bigwedge_\subbox{j \in J'_{23x} \cap H} \beta_{1j} = \beta_{2xj} \Rightarrow  \bigwedge_\subbox{j \in (J'_{2x} \cap H)\uplus J_3} \beta_{13j} = \beta_{23xj}}$\\
+Because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.
+By building  $t_{13}$ and $t_{23}$ we have $\alpha_{13}=
+\alpha_{1}$ and $\alpha_{23x}=\alpha_{2x}$. So we deduce: 
+$\alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$.\\
+We have also:\\ $\beta_{13j}^{J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
+and $\beta_{23xj}^{J'_{23}}= \beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }$\\
+As $t_{13}$ and $t_{23}$ are built with the same transitions of $A_3$  (up renaming) so we can deduce:
+\begin{align*}
+{\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}} & \Rightarrow  {\displaystyle \bigwedge_\subbox{j \in (J'_{2x} \setminus \{k\}  \cap H)\uplus J^{2 \prime}_3} \beta_{13j} = \beta_{23xj}}\\
+& \Rightarrow {\displaystyle \bigwedge_\subbox{j \in (J'_{2x} \setminus \{k\}  \cap H)\uplus J^{2 \prime}_3 } \beta_{13j} = \beta_{23xj}}\\
+\end{align*}
 On another side,   the composition gives $g_{13} \Leftrightarrow g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}$ and
 $g_{23x}  \Leftrightarrow g_{2x} \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk}$. \\
-In addition $k \in H$ we have   
+In addition as $k \in H$ we have   
 $\beta_{1k} = \beta_{2xk}$ then we  deduce:

### 2022-02-14 2021-Refinement/paper/refinementarticle.tex
part...

@@
 and $\beta_{23xj}^{J'_{23}}= \beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }$\\
-As $t_{13}$ and $t_{23}$ are built with the same transitions of $A_3$  (up renaming) so we can deduce:
-\begin{align*}
-{\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}} & \Rightarrow  {\displaystyle \bigwedge_\subbox{j \in (J'_{2x} \setminus \{k\}  \cap H)\uplus J^{2 \prime}_3} \beta_{13j} = \beta_{23xj}}\\
-& \Rightarrow {\displaystyle \bigwedge_\subbox{j \in (J'_{2x} \setminus \{k\}  \cap H)\uplus J^{2 \prime}_3 } \beta_{13j} = \beta_{23xj}}\\
+So we have:  $\beta_{13j} = \beta_{23xj} \Rightarrow (\beta_{1j} = \beta_{2xj}) \vee (\beta^1_{3j}= \beta^2_{3j})$\\
+Considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up  renaming) hence we have: $V^1_{3} \uplus V^2_{3}  \vdash {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$\\
+
+Assuming we have $V_{1} \uplus V_{2} \uplus \fvars{t_1}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}}$ then we can deduce:
+\begin{align*}
+& V_{1} \uplus V_{2}  \uplus V^1_{3} \uplus V^2_{3} \uplus \fvars{t_1}\vdash  {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}} \vee {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}\\
+\Rightarrow & V_{13} \uplus V_{23}  \uplus \fvars{t_1}\vdash {\displaystyle \bigwedge_\subbox{j \in (J'_{2x}   \cap H)\uplus J^{2 \prime}_3 } \beta_{13j} = \beta_{23xj}} \\  
+\Rightarrow & V_{13} \uplus V_{23}  \uplus \fvars{t_1}\vdash {\displaystyle \bigwedge_\subbox{j \in \Rightarrow   ((J'_{2x}   \cap H)\uplus J^{2 \prime}_3)\setminus \{k\} } \beta_{13j} = \beta_{23xj}} \\
+\Rightarrow &  V_{13} \uplus V_{23}  \uplus \fvars{t_1}\vdash {\displaystyle \bigwedge_\subbox{j \in (J'_{23x}   \cap H') } \beta_{13j} = \beta_{23xj}}\\
 \end{align*}
@@
 
-By adding the same (and equivalent) terms  to both sides of the implication of the formula $(*)$,  and  from all the implications induced by the extension of the valuation context mentioned above, we get:
-\begin{multline*}
-V_1 \uplus V_2 \uplus \fvars{t_1} \uplus V^1_3  \uplus V^2_3 \vdash\\
+From all the implications induced by the extension of the valuation context mentioned above, and by entering   all previous intermediate results in the formula $(*)$, we get:
+\begin{multline*}
+V_{13} \uplus V_{23}  \uplus \fvars{t_1} \vdash\\
 R\mpar{s_1, s_{2}} \wedge g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k} %\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
@@
 \begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in (J'_{2x} \cap H)\uplus J_3} \beta_{13j}\! =\! \beta_{23xj}\\
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in (J'_{23x} \cap H')} \beta_{13j}\! =\! \beta_{23xj}\\
 			 \nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}

### 2022-02-22 2021-Refinement/paper/refinementarticle.tex
proof thm2

@@
 \item if $k \in J'_1$:\\
-Because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.
+The proof is based on the following facts.
+First, because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.
 By building  $t_{13}$ and $t_{23}$ we have $\alpha_{13}=
@@
 $\alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$.\\
-We have also:\\ $\beta_{13j}^{J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
+Second, we have:\\ $\beta_{13j}^{J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
 and $\beta_{23xj}^{J'_{23}}= \beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }$\\
-So we have:  $\beta_{13j} = \beta_{23xj} \Rightarrow (\beta_{1j} = \beta_{2xj}) \vee (\beta^1_{3j}= \beta^2_{3j})$\\
-Considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up  renaming) hence we have: $V^1_{3} \uplus V^2_{3}  \vdash {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$\\
-
-Assuming we have $V_{1} \uplus V_{2} \uplus \fvars{t_1}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}}$ then we can deduce:
-\begin{align*}
-& V_{1} \uplus V_{2}  \uplus V^1_{3} \uplus V^2_{3} \uplus \fvars{t_1}\vdash  {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}} \vee {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}\\
-\Rightarrow & V_{13} \uplus V_{23}  \uplus \fvars{t_1}\vdash {\displaystyle \bigwedge_\subbox{j \in (J'_{2x}   \cap H)\uplus J^{2 \prime}_3 } \beta_{13j} = \beta_{23xj}} \\  
-\Rightarrow & V_{13} \uplus V_{23}  \uplus \fvars{t_1}\vdash {\displaystyle \bigwedge_\subbox{j \in \Rightarrow   ((J'_{2x}   \cap H)\uplus J^{2 \prime}_3)\setminus \{k\} } \beta_{13j} = \beta_{23xj}} \\
-\Rightarrow &  V_{13} \uplus V_{23}  \uplus \fvars{t_1}\vdash {\displaystyle \bigwedge_\subbox{j \in (J'_{23x}   \cap H') } \beta_{13j} = \beta_{23xj}}\\
-\end{align*}
-On another side,   the composition gives $g_{13} \Leftrightarrow g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}$ and
+Therefore, we have:  $\beta_{13j} = \beta_{23xj} \Rightarrow (\beta_{1j} = \beta_{2xj}) \vee (\beta^1_{3j}= \beta^2_{3j})$\\
+Third, considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up  renaming) hence we have: $V^1_{3} \uplus V^2_{3}  \vdash {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$\\
+And suppose that  $V_{1} \uplus V_{2} \uplus \fvars{t_1}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}}$ holds then we can deduce:
+\begin{align*}
+& V_{1} \uplus V_{2}  \uplus V^1_{3} \uplus V^2_{3} \uplus \fvars{t_1}\vdash  & {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}} \vee {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}\\
+\Rightarrow & V_{13} \uplus V_{23}  \uplus \fvars{t_1}\vdash & {\displaystyle \bigwedge_\subbox{j \in (J'_{2x}   \cap H)\uplus J^{2 \prime}_3 } \beta_{13j} = \beta_{23xj}} \\  
+\Rightarrow & V_{13} \uplus V_{23}  \uplus \fvars{t_1}\vdash & {\displaystyle \bigwedge_\subbox{j \in \Rightarrow   ((J'_{2x}   \cap H)\uplus J^{2 \prime}_3)\setminus \{k\} } \beta_{13j} = \beta_{23xj}} \\
+\Rightarrow &  V_{13} \uplus V_{23}  \uplus \fvars{t_1}\vdash & {\displaystyle \bigwedge_\subbox{j \in (J'_{23x}   \cap H') } \beta_{13j} = \beta_{23xj}}\\
+\end{align*}
+Finally, the composition gives $g_{13} \Leftrightarrow g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}$ and
 $g_{23x}  \Leftrightarrow g_{2x} \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk}$. \\
-In addition as $k \in H$ we have   
+Furthermore, as $k \in H$ we have   
 $\beta_{1k} = \beta_{2xk}$ then we  deduce:
 $g^1_3 \wedge \alpha^1_3=\beta_{1k}  \Leftrightarrow g^2_3 \wedge \alpha^2_3= \beta_{2xk}$
-
-\TODO{The subtlety here is that the original relation implies that valuations in A3 are equal (ie the value for each variable are the same in both valuations, modulo renaming), after a transition we should obtain ``equal'' valuations because Post are deterministic}
 
@@
 \begin{multline*}
-V_{13} \uplus V_{23} \uplus \fvars{t_1}  \uplus \fvars{t_{13}} \vdash\\
+V_{13} \uplus V_{23} \uplus \fvars{t_1}  \cap \fvars{t_{13}} \vdash\\
 R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \reach{A_{13}}\mpar{s_{13}}
@@
 \end{multline*}	
-
-Considering that ate each step the valuations $\sigma_{3}^1$ and $\sigma_{3}^2$ associate the same values to the ``same'' variables modulo renaming, we have the tautology:\\ $\left({\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{3}^1 \uplus \sigma_{3}^2 }$.
-
+\TODO{The subtlety here is that the original relation implies that valuations in A3 are equal (ie the value for each variable are the same in both valuations, modulo renaming), after a transition we should obtain ``equal'' valuations because Post are deterministic}
+
+Considering that at each step the valuations $\sigma_{3}^1$ and $\sigma_{3}^2$ associate the same values to the ``same'' variables modulo renaming, so for any states $s^1_3$ and $s^2_3$ the following formula is a tautology:\\ $\left({\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{3}^1 \uplus \sigma_{3}^2 }$ which is equivalent to \\
+$V_3^1 \uplus V_3^2 \vdash \left({\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)$ \\
+By adding tautologies to both members of the implication, we get:
+\begin{multline*}
+V_{13} \uplus V_{23} \uplus \fvars{t_1}  \cap \fvars{t_{13}} \vdash\\
+R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \reach{A_{13}}\mpar{s_{13}}
+\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
+\implies \hspace{5em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge \\
+			g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
+\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^{1\prime}_3=s^{2\prime}_3
+		\end{array}}   
+\end{multline*}	
+\TODO{Point a verifier!}
+\item if $k \notin J'_1$:\\
+The first and second arguments remain the same as the previous case, while for the third we have: $g_{13} \Leftrightarrow g_1$ and
+$g_{23x}  \Leftrightarrow g_{2x} $. By replacing  these results in the formula $(*)$, we get the same formula:
+\begin{multline*}
+V_{13} \uplus V_{23} \uplus \fvars{t_1}  \vdash\\
+R\mpar{s_1, s_{2}} \wedge g_{13}  
+%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
+\implies  \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\
+			\nwedge g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
+		\end{array}}   
+\end{multline*}	
+From this point on, the proof continues as in the previous case.\\
 \end{itemize}
 
-\newpage
-%%%%%%%%%%%%%%%%%%%%%%%%%%%555
-
-\TODO{Pas termine: valider d'abord la definition de R}
-\item The last formula to prove is the following:
-\begin{multline*}
-\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23},\\ V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_2} \vdash \left(R\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_1 \in \fOT{s_{13}}} \fguard{t_{13}} \right)
-\end{multline*}
-By hypothesis we have the following:
-\begin{multline*}
-\forall \mpar{s_1, s_2} \in S_1 \times S_2,\\ V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
-\end{multline*}
-By adding the term $\displaystyle{\bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3}}$ to both sides of the implication, we get: 
-\begin{multline*}
-\forall \mpar{s_1, s_2,s_3} \in S_1 \times S_2 \times S_3, V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3}\right)
-\end{multline*}
-By hypothesis we also have \(A_1\subst{A_3}{k}\) is non-blocking,  thus we can write the following:
-\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
+\item The last formula we need to prove is the following: for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
+\begin{multline*}
+V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_{23}} \vdash \left(R^{\prime}\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_1 \in \fOT{s_{13}}} \fguard{t_{13}} \right)
+\end{multline*}
+Let's start  with the hypothesis of the theorem that $\wrel{A_1}{A_2}{H}$, thus we have for all  $\mpar{s_1, s_2} \in S_1 \times S_2$ 
+\begin{multline*}
+V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
+\end{multline*}
+By adding  the same term to both members of the implication, we get:
+\begin{multline*}
+V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \\\left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \wedge  \reach{A_{13}}\mpar{s_{13}}\implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}  \wedge \reach{A_{13}}\mpar{s_{13}}\right)
+\end{multline*}
+But by hypothesis we have also the result of the composition \(A_1\subst{A_3}{k}\) is non-blocking, which leads to:
+\begin{multline*}
+V_{13}  \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \left( \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \right)
+\end{multline*}
+
 \end{enumerate}

### 2022-02-23 2021-Refinement/paper/refinementarticle.tex
work on proof of thm 2

@@
 Let us denote by $A_{13}$ (resp.
-$A_{23}$) the open automaton resulting from $A_1\subst{A_3}{k}$ ($A_2\subst{A_3}{k}$),  to prove the theorem it sufficient to prove that there exists a relation between states of the two open automata that satisfies the conditions of the Definition \ref{Def:OA-Refinement}.
-The proof requires to resort to rename the elements (states, variables, etc) of an automaton according to the one to which they belong.
-
-We denote $A_1=  \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}$ and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and $A_3 = \OA{S_3}{s_{03}}{J_3}{V_3}{\sigma_{03}}{T_3}$
+$A_{23}$) the open automaton resulting from $A_1\subst{A_3}{k}$ (resp.
+$A_2\subst{A_3}{k}$),  to prove the theorem it sufficient to prove that there exists a relation between states of the two open automata that satisfies the conditions of the Definition \ref{Def:OA-Refinement}.
+
+We denote $A_1=  \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}$ and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and $A_3 = \OA{S_3}{s_{03}}{J_3}{V_3}{\sigma_{03}}{T_3}$.
+The proof requires  to rename the variables of one instance of the two $A_3$ automata to avoid clashes in variable names (this is required by the definition of refinement).
+In practice we will use superscripts ${}^1$ and ${}^2$ to distinguish elements of the two instances of $A_3$.
 
@@
 
-We want to prove that $\mpar{R', H\uplus J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$. In the following we denote $H'=H\cup J_3 \setminus\{k\}$
+We want to prove that $\mpar{R', H\uplus J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$. In the following we denote $H'=H\cup J_3 \setminus\{k\}$.
 \begin{enumerate}
-\item First, we have to prove the following:
+\item First, we have to prove the relation for initial states:
 \[\sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}\]
@@
 
-\item We need to prove for any OT $t_{13}$ in $T_{13}$ originating from $s_{13}$:
+\item Second, we need to prove for any OT $t_{13}$ in $T_{13}$ originating from $s_{13}$:
 \begin{align*}
@@
 \end{align*}		
-there exists an indexed family $t_{23x}$ of OTs originating from $s_{23}$: 
+there exists an indexed family $t_{23x}$ of OTs originating from $s_{23}$ that simulates it: 
 \begin{align*}
@@
 	\end{align*}
-Recall that 
+By definition of composition and open automata refinement we have: 
 \begin{align*}
@@
 First, because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.
-By building  $t_{13}$ and $t_{23}$ we have $\alpha_{13}=
+By construction of  $t_{13}$ and $t_{23}$ we have $\alpha_{13}=
 \alpha_{1}$ and $\alpha_{23x}=\alpha_{2x}$. So we deduce: 
 $\alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$.\\
-Second, we have:\\ $\beta_{13j}^{J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
+Second, we have: \TODO{discuss next equations}\\ $\beta_{13j}^{J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
 and $\beta_{23xj}^{J'_{23}}= \beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }$\\
 Therefore, we have:  $\beta_{13j} = \beta_{23xj} \Rightarrow (\beta_{1j} = \beta_{2xj}) \vee (\beta^1_{3j}= \beta^2_{3j})$\\
-Third, considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up  renaming) hence we have: $V^1_{3} \uplus V^2_{3}  \vdash {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$\\
+Third, considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up to renaming)  we have: $V^1_{3} \uplus V^2_{3}  \vdash {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$ \TODO{No, rather:}\\
+${\displaystyle V^1_{3} \uplus V^2_{3}  \vdash \bigwedge_\subbox{v_3\in \fvars{s_{3}}
+}\!\!\! v^1_3=v^2_3\implies \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$
+
+\TODO{adapt}
+
 And suppose that  $V_{1} \uplus V_{2} \uplus \fvars{t_1}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}}$ holds then we can deduce:

### 2022-02-23 2021-Refinement/paper/refinementarticle.tex
meeting notes

@@
 $\alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$.\\
-Second, we have: \TODO{discuss next equations}\\ $\beta_{13j}^{J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
-and $\beta_{23xj}^{J'_{23}}= \beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }$\\
-Therefore, we have:  $\beta_{13j} = \beta_{23xj} \Rightarrow (\beta_{1j} = \beta_{2xj}) \vee (\beta^1_{3j}= \beta^2_{3j})$\\
+Second, we have: \\ $\beta_{13j}^{j\in J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
+and $\beta_{23xj}^{j\in J'_{23}}= \beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }$\\
+Therefore, we have for all $j\in J'_{13}$ (recall that $J'_{13}=J'_{23}$):  \[\beta_{13j} = \beta_{23xj} \Rightarrow (j\in J_1 \land \beta_{1j} = \beta_{2xj}) \vee (j\in J_3^1 \land \beta^1_{3j}= \beta^2_{3j})\]\\
 Third, considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up to renaming)  we have: $V^1_{3} \uplus V^2_{3}  \vdash {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$ \TODO{No, rather:}\\
@@
 \begin{align*}
-& V_{1} \uplus V_{2}  \uplus V^1_{3} \uplus V^2_{3} \uplus \fvars{t_1}\vdash  & {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}} \vee {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}\\
+& V_{1} \uplus V_{2}  \uplus V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}}\vdash  & {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}} \vee {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}\\
 \Rightarrow & V_{13} \uplus V_{23}  \uplus \fvars{t_1}\vdash & {\displaystyle \bigwedge_\subbox{j \in (J'_{2x}   \cap H)\uplus J^{2 \prime}_3 } \beta_{13j} = \beta_{23xj}} \\  
@@
 V_{13} \uplus V_{23} \uplus \fvars{t_1}  \vdash\\
+\bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3 \land
 R\mpar{s_1, s_{2}} \wedge g_{13}  

### 2022-03-01 2021-Refinement/paper/refinementarticle.tex
point 2 termine

--- 2022-02-23 2021-Refinement/paper/refinementarticle.tex
@@
 $\alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$.\\
-Second, we have: \TODO{discuss next equations}\\ $\beta_{13j}^{J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
-and $\beta_{23xj}^{J'_{23}}= \beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }$\\
-Therefore, we have:  $\beta_{13j} = \beta_{23xj} \Rightarrow (\beta_{1j} = \beta_{2xj}) \vee (\beta^1_{3j}= \beta^2_{3j})$\\
-Third, considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up to renaming)  we have: $V^1_{3} \uplus V^2_{3}  \vdash {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$ \TODO{No, rather:}\\
-${\displaystyle V^1_{3} \uplus V^2_{3}  \vdash \bigwedge_\subbox{v_3\in \fvars{s_{3}}
+Second, we have: \\ $\beta_{13j}^{j\in J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
+and $\beta_{23xj}^{j\in J'_{23}}= \beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }$\\
+Therefore, we have for all $j\in J'_{13}$ (recall that $J'_{13}=J'_{23}$):  \[\beta_{13j} = \beta_{23xj} \Rightarrow (j\in J_1 \land \beta_{1j} = \beta_{2xj}) \vee (j\in J_3^1 \land \beta^1_{3j}= \beta^2_{3j})\]\\
+Third, considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up to renaming)  we have: 
+${\displaystyle V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}} \vdash \bigwedge_\subbox{v_3\in \fvars{s_{3}}
 }\!\!\! v^1_3=v^2_3\implies \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$
 
-\TODO{adapt}
-
 And suppose that  $V_{1} \uplus V_{2} \uplus \fvars{t_1}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}}$ holds then we can deduce:
 \begin{align*}
-& V_{1} \uplus V_{2}  \uplus V^1_{3} \uplus V^2_{3} \uplus \fvars{t_1}\vdash  & {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}} \vee {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}\\
-\Rightarrow & V_{13} \uplus V_{23}  \uplus \fvars{t_1}\vdash & {\displaystyle \bigwedge_\subbox{j \in (J'_{2x}   \cap H)\uplus J^{2 \prime}_3 } \beta_{13j} = \beta_{23xj}} \\  
-\Rightarrow & V_{13} \uplus V_{23}  \uplus \fvars{t_1}\vdash & {\displaystyle \bigwedge_\subbox{j \in \Rightarrow   ((J'_{2x}   \cap H)\uplus J^{2 \prime}_3)\setminus \{k\} } \beta_{13j} = \beta_{23xj}} \\
-\Rightarrow &  V_{13} \uplus V_{23}  \uplus \fvars{t_1}\vdash & {\displaystyle \bigwedge_\subbox{j \in (J'_{23x}   \cap H') } \beta_{13j} = \beta_{23xj}}\\
+ V_{1} \uplus V_{2}  \uplus V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}}\vdash &    \bigwedge_\subbox{v_3\in \fvars{s_{3}}
+}\!\!\! v^1_3=v^2_3 \implies {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}} \vee {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}\\
+\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in \fvars{s_{3}}
+}\!\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{2x}   \cap H)\uplus J^{2 \prime}_3 } \beta_{13j} = \beta_{23xj}} \\  
+\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in \fvars{s_{3}}
+}\!\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in \Rightarrow   ((J'_{2x}   \cap H)\uplus J^{2 \prime}_3)\setminus \{k\} } \beta_{13j} = \beta_{23xj}} \\
+\Rightarrow    V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in \fvars{s_{3}}
+}\!\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{23x}   \cap H') } \beta_{13j} = \beta_{23xj}}\\
 \end{align*}
@@
 \begin{multline*}
-V_{13} \uplus V_{23}  \uplus \fvars{t_1} \vdash\\
-R\mpar{s_1, s_{2}} \wedge g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k} %\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
+V_{13} \uplus V_{23}  \uplus \fvars{t_{13}} \vdash\\
+R\mpar{s_1, s_{2}} \wedge \mpar{g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}}\wedge \bigwedge_\subbox{v_3\in \fvars{s_3}}  v^1_3=v^2_3 %\wedge s^1_3=s^2_3
 \implies  \hspace{12em}\\
@@
 \begin{multline*}
-V_{13} \uplus V_{23} \uplus \fvars{t_1}  \vdash\\
-R\mpar{s_1, s_{2}} \wedge g_{13}  
-%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
+V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
+R\mpar{s_1, s_{2}} \wedge g_{13}  \land \bigwedge_\subbox{v_3\in \fvars{s_3}} v^1_3=v^2_3
 \implies  \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
@@
 			\nwedge g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
-		\end{array}}   
-\end{multline*}
-
-By hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
+		\end{array}}   
+\end{multline*}	
+\TODO{The subtlety here is that the original relation implies that valuations in A3 are equal (ie the value for each variable are the same in both valuations, modulo renaming), after a transition we should obtain ``equal'' valuations because Post are deterministic}
+
+We can write:
+\begin{multline*}
+V_{13} \uplus V_{23}  \uplus \fvars{t_{13}} \vdash\\
+\bigwedge_\subbox{v_3\in \fvars{s_{3}}
+}\!\!\! v^1_3=v^2_3  \wedge s^1_3 = s^2_3 \implies \bigwedge_\subbox{v_3\in \fvars{s^{\prime}_{3}}
+}\!\!\! v^1_3=v^2_3  \wedge s^{1\prime}_3 = s^{2\prime}_3 
+ \end{multline*}	
+Therefore, we get:
+\begin{multline*}
+V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
+R\mpar{s_1, s_{2}} \wedge g_{13}  \land \bigwedge_\subbox{v_3\in \fvars{s_3}} v^1_3=v^2_3 \wedge s^1_3 = s^2_3
+\implies \hspace{7em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\
+			\nwedge g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \bigwedge_\subbox{v_3\in \fvars{s^{\prime}_{3}}
+}\!\!\! v^1_3=v^2_3  \wedge s^{1\prime}_3 = s^{2\prime}_3
+		\end{array}}   
+\end{multline*}
+And finally By hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
 \[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
-From these two previous formulas we obtain:
+Thus, we get:
 \begin{multline*}
@@
 R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \reach{A_{13}}\mpar{s_{13}}
-%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
-\implies  \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\
-			\nwedge g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} 
-%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
-		\end{array}}   \wedge \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
-\end{multline*}	
-\TODO{The subtlety here is that the original relation implies that valuations in A3 are equal (ie the value for each variable are the same in both valuations, modulo renaming), after a transition we should obtain ``equal'' valuations because Post are deterministic}
-
-Considering that at each step the valuations $\sigma_{3}^1$ and $\sigma_{3}^2$ associate the same values to the ``same'' variables modulo renaming, so for any states $s^1_3$ and $s^2_3$ the following formula is a tautology:\\ $\left({\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{3}^1 \uplus \sigma_{3}^2 }$ which is equivalent to \\
-$V_3^1 \uplus V_3^2 \vdash \left({\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)$ \\
-By adding tautologies to both members of the implication, we get:
-\begin{multline*}
-V_{13} \uplus V_{23} \uplus \fvars{t_1}  \cap \fvars{t_{13}} \vdash\\
-R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \reach{A_{13}}\mpar{s_{13}}
-\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
+\wedge \bigwedge_\subbox{v_3\in \fvars{s_3}}  v^1_3=v^2_3\wedge s^1_3=s^2_3
 \implies \hspace{5em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
@@
 			g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
-\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^{1\prime}_3=s^{2\prime}_3
-		\end{array}}   
-\end{multline*}	
-\TODO{Point a verifier!}
+\wedge \bigwedge_\subbox{v_3\in \fvars{s^{\prime}_3}}  v^1_3=v^2_3\wedge s^{1\prime}_3=s^{2\prime}_3
+		\end{array}}   
+\end{multline*}	
+Because of the domain of the substitutions of the relations, we get expected formula:\TODO{Point a verifier les substitutions!}
+	\begin{multline*}
+  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ R^{\prime}\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
+			\nwedge g_{23x} \wedge R^{\prime}\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
+		\end{array}} 
+	\end{multline*}
+
 \item if $k \notin J'_1$:\\
-The first and second arguments remain the same as the previous case, while for the third we have: $g_{13} \Leftrightarrow g_1$ and
-$g_{23x}  \Leftrightarrow g_{2x} $. By replacing  these results in the formula $(*)$, we get the same formula:
-\begin{multline*}
-V_{13} \uplus V_{23} \uplus \fvars{t_1}  \vdash\\
-R\mpar{s_1, s_{2}} \wedge g_{13}  
-%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
-\implies  \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\
-			\nwedge g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
-		\end{array}}   
-\end{multline*}	
-From this point on, the proof continues as in the previous case.\\
+The proof of this case follows the same steps as the previous case the only argument that changes is that  $g_{13} \Leftrightarrow g_1$ and
+$g_{23x}  \Leftrightarrow g_{2x}$.
  \end{itemize}
-
 \item The last formula we need to prove is the following: for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
 \begin{multline*}
-V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_{23}} \vdash \left(R^{\prime}\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_1 \in \fOT{s_{13}}} \fguard{t_{13}} \right)
-\end{multline*}
-Let's start  with the hypothesis of the theorem that $\wrel{A_1}{A_2}{H}$, thus we have for all  $\mpar{s_1, s_2} \in S_1 \times S_2$ 
+V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_{23}} \vdash \\ \left(R^{\prime}\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_1 \in \fOT{s_{13}}} \fguard{t_{13}} \right)
+\end{multline*}
+Let's start  with the hypothesis of the theorem stating that $\wrel{A_1}{A_2}{H}$, thus we have for all  $\mpar{s_1, s_2} \in S_1 \times S_2$ 
 \begin{multline*}
@@
 \end{multline*}
-
  \end{enumerate}

### 2022-03-04 2021-Refinement/paper/refinementarticle.tex
proof in progress

@@
 
+~\qed
+
 \section{Proof of Context Refinement}
@@
 $A_{23}$) the open automaton resulting from $A_1\subst{A_3}{k}$ (resp.
-$A_2\subst{A_3}{k}$),  to prove the theorem it sufficient to prove that there exists a relation between states of the two open automata that satisfies the conditions of the Definition \ref{Def:OA-Refinement}.
+$A_2\subst{A_3}{k}$),  to prove the theorem it is sufficient to prove that there exists a relation between states of the two open automata that satisfies the conditions of the Definition \ref{Def:OA-Refinement}.
 
@@
 
-We can write:
+We can deduce for any transition $t_3$ in $A_3$ relying $s_3$ and $s^{\prime}_3$ we have:
 \begin{multline*}
@@
 \end{multline*}
-By adding  the same term to both members of the implication, we get:
-\begin{multline*}
-V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \\\left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \wedge  \reach{A_{13}}\mpar{s_{13}}\implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}  \wedge \reach{A_{13}}\mpar{s_{13}}\right)
-\end{multline*}
-But by hypothesis we have also the result of the composition \(A_1\subst{A_3}{k}\) is non-blocking, which leads to:
+We have a second hypothesis stating that the result of the composition \(A_1\subst{A_3}{k}\) is non-blocking, which leads to:
 \begin{multline*}
@@
 \end{multline*}
+We use the the first, we extend the valuation to cover the variables of  $t^2_3$ in $t_{23}$ using their value in $t_3$ and because $\fvars{t_{13}} \vdash \reach{A_{13}}\mpar{s_{13}}$, we get"
+\begin{multline*}
+V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}  \wedge \reach{A_{13}}\mpar{s_{13}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}   \wedge \reach{A_{13}}\mpar{s_{13}}\right)
+\end{multline*}
+By transitivity with the second hypothesis we obtain:
+\begin{multline*}
+V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}   \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}\right)
+\end{multline*}
+\TODO{verifier les contextes valuations} \qed
  \end{enumerate}
+
+\section{Proof of Congruence}
+
+\proof
+Let us denote by $A_{12}$ (resp.
+$A_{13}$) the open automaton resulting from $A_1\subst{A_2}{k}$ (resp.
+$A_1\subst{A_3}{k}$),  to prove the theorem it is sufficient to prove that there exists a relation between states of the two open automata that satisfies the conditions of the Definition \ref{Def:OA-Refinement}.
+
+We denote $A_1=  \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}$ and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and $A_3 = \OA{S_3}{s_{03}}{J_3}{V_3}{\sigma_{03}}{T_3}$.
+
+% The proof requires  to rename the variables of one instance of the two $A_3$ automata to avoid clashes in variable names (this is required by the definition of refinement).
+In practice we will use superscripts ${}^1$ and ${}^2$ to distinguish elements of the two instances of $A_3$.
+ \qed
 

### 2022-03-07 2021-Refinement/paper/refinementarticle.tex
proof of thm

@@
 We define a relation $R'$ relating states of $s_{13}$ and $s_{23}$ as follows:
-\[ R' \mpar{s_{13}, s_{23}} = R\mpar{s_{1}, s_{2}} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigwedge_\subbox{v_3\in \fvars{s_{3}}
-}\!\!\! v^1_3=v^2_3\wedge s^1_3 = s^2_3\]
+\[ R' \mpar{s_{13}, s_{23}} = R\mpar{s_{1}, s_{2}} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigwedge_\subbox{v_3\in V_3}
+\!\!\! v^1_3=v^2_3\wedge s^1_3 = s^2_3\]
 
@@
 \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
-\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \land \bigwedge_\subbox{v_3\in vars(s_3)} v^1_3=v^2_3\wedge s^1_3 = s^2_3\\
-\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v_3\in vars(s_3)}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma^1_{03}\uplus \sigma^2_{03} }\\
+\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3\\
+\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma^1_{03}\uplus \sigma^2_{03} }\\
 \implies & \sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}
@@
 Third, considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up to renaming)  we have: 
-${\displaystyle V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}} \vdash \bigwedge_\subbox{v_3\in \fvars{s_{3}}
-}\!\!\! v^1_3=v^2_3\implies \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$
+${\displaystyle V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}} \vdash \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$
 
@@
 \begin{align*}
- V_{1} \uplus V_{2}  \uplus V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}}\vdash &    \bigwedge_\subbox{v_3\in \fvars{s_{3}}
-}\!\!\! v^1_3=v^2_3 \implies {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}} \vee {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}\\
-\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in \fvars{s_{3}}
-}\!\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{2x}   \cap H)\uplus J^{2 \prime}_3 } \beta_{13j} = \beta_{23xj}} \\  
-\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in \fvars{s_{3}}
-}\!\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in \Rightarrow   ((J'_{2x}   \cap H)\uplus J^{2 \prime}_3)\setminus \{k\} } \beta_{13j} = \beta_{23xj}} \\
-\Rightarrow    V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in \fvars{s_{3}}
-}\!\!\! v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{23x}   \cap H') } \beta_{13j} = \beta_{23xj}}\\
+ V_{1} \uplus V_{2}  \uplus V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}}\vdash &    \bigwedge_\subbox{v_3\in V_3}\!\!
+v^1_3=v^2_3 \implies {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}} \vee {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}\\
+\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\!
+v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{2x}   \cap H)\uplus J^{2 \prime}_3 } \beta_{13j} = \beta_{23xj}} \\
+\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\!
+v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in \Rightarrow   ((J'_{2x}   \cap H)\uplus J^{2 \prime}_3)\setminus \{k\} } \beta_{13j} = \beta_{23xj}} \\
+\Rightarrow    V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\!
+v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{23x}   \cap H') } \beta_{13j} = \beta_{23xj}}\\
 \end{align*}
@@
 V_{13} \uplus V_{23}  \uplus \fvars{t_{13}} \vdash\\
-R\mpar{s_1, s_{2}} \wedge \mpar{g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}}\wedge \bigwedge_\subbox{v_3\in \fvars{s_3}}  v^1_3=v^2_3 %\wedge s^1_3=s^2_3
+R\mpar{s_1, s_{2}} \wedge \mpar{g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}}\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3 %\wedge s^1_3=s^2_3
 \implies  \hspace{12em}\\
@@
 V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
-R\mpar{s_1, s_{2}} \wedge g_{13}  \land \bigwedge_\subbox{v_3\in \fvars{s_3}} v^1_3=v^2_3
+R\mpar{s_1, s_{2}} \wedge g_{13}  \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3
 \implies  \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
@@
 V_{13} \uplus V_{23}  \uplus \fvars{t_{13}} \vdash\\
-\bigwedge_\subbox{v_3\in \fvars{s_{3}}
-}\!\!\! v^1_3=v^2_3  \wedge s^1_3 = s^2_3 \implies \bigwedge_\subbox{v_3\in \fvars{s^{\prime}_{3}}
-}\!\!\! v^1_3=v^2_3  \wedge s^{1\prime}_3 = s^{2\prime}_3 
+\bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3  \wedge s^1_3 = s^2_3 \implies \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3)  \wedge s^{1\prime}_3 = s^{2\prime}_3 
  \end{multline*}	
@@
 V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
-R\mpar{s_1, s_{2}} \wedge g_{13}  \land \bigwedge_\subbox{v_3\in \fvars{s_3}} v^1_3=v^2_3 \wedge s^1_3 = s^2_3
+R\mpar{s_1, s_{2}} \wedge g_{13}  \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3 \wedge s^1_3 = s^2_3
 \implies \hspace{7em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
 \begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\
-			\nwedge g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \bigwedge_\subbox{v_3\in \fvars{s^{\prime}_{3}}
-}\!\!\! v^1_3=v^2_3  \wedge s^{1\prime}_3 = s^{2\prime}_3
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\\
+			 \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+\land \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3) \wedge s^{1\prime}_3 = s^{2\prime}_3
 		\end{array}}   
@@
 \begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge \\
-			g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
-\wedge \bigwedge_\subbox{v_3\in \fvars{s^{\prime}_3}}  v^1_3=v^2_3\wedge s^{1\prime}_3=s^{2\prime}_3
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge 	g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\\
+		  \wedge \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
+\wedge \bigwedge_\subbox{v_3\in V_3}  \psi_{13}(v^1_3)=\psi_{13}(v^2_3)\wedge s^{1\prime}_3=s^{2\prime}_3
 		\end{array}}   

### 2022-03-07 2021-Refinement/paper/refinementarticle.tex
proof thm 3

@@
 \end{align*}
-there exist an indexed family of OTs originating from $s_3$: 
+there exists an indexed family of OTs originating from $s_3$: 
 \begin{align*}
@@
 \[ R' \mpar{s_{13}, s_{23}} = R\mpar{s_{1}, s_{2}} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigwedge_\subbox{v_3\in V_3}
-\!\!\! v^1_3=v^2_3\wedge s^1_3 = s^2_3\]
+ v^1_3=v^2_3\wedge s^1_3 = s^2_3\]
 
@@
 
-Considering that initial valuations $\sigma_{03}^1$ and $\sigma_{03}^2$ associate the same values to the ``same'' variables modulo renaming, we have the tautology:\\ $\left(\,\,\,\,{\displaystyle \bigwedge_\subbox{v_3\in vars(s_3)} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }$.
+Considering that initial valuations $\sigma_{03}^1$ and $\sigma_{03}^2$ associate the same values to the ``same'' variables modulo renaming, we have the tautology:\\ $\left(\,\,{\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }$.
 
@@
 \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
-\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3\\
-\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma^1_{03}\uplus \sigma^2_{03} }\\
+\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \land \mpar{\bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }\\
+\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma^1_{03}\uplus \sigma^2_{03}\uplus \sigma_{013} }\\
 \implies & \sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}
@@
  J'_{13} \cap H'} \text{ and }\\
-		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ & R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
 			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
@@
 \Rightarrow    V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\!
-v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{23x}   \cap H') } \beta_{13j} = \beta_{23xj}}\\
+v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{23x}   \cap H') } \beta_{13j} = \beta_{23xj}}
 \end{align*}
@@
 \begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\\
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\land\\
 			 \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-\land \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3) \wedge s^{1\prime}_3 = s^{2\prime}_3
+ \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3) \wedge s^{1\prime}_3 = s^{2\prime}_3
 		\end{array}}   
@@
 R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \reach{A_{13}}\mpar{s_{13}}
-\wedge \bigwedge_\subbox{v_3\in \fvars{s_3}}  v^1_3=v^2_3\wedge s^1_3=s^2_3
+\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
 \implies \hspace{5em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
@@
 \end{multline*}	
-Because of the domain of the substitutions of the relations, we get expected formula:\TODO{Point a verifier les substitutions!}
+Because of the independence of the substitution domains, we get the expected formula:
 	\begin{multline*}
@@
 \end{multline*}
-\TODO{verifier les contextes valuations} \qed
+That implies:
+\begin{multline*}
+V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(\underbrace{R\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3}_{R^{\prime}(s_{13},s_{23})}  \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}   \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}\right)
+\end{multline*}
+which gives us what we needed to demonstrate. \qed
  \end{enumerate}
@@
 In practice we will use superscripts ${}^1$ and ${}^2$ to distinguish elements of the two instances of $A_3$.
- \qed
+
+Let $R$ be the refinement relation relating states of $A_2$ and $A_3$. 
+Let us denote with $t^2$ and $t^3$  the elements of $A_2$ and $A_3$ respectively.
+Consider any two states $s_{12} = \mpar{s_1,s^1_2}$ and $s_{13} = \mpar{s^2_1,s_3}$ ($s^1_1$ and $s^2_1$  are the same with renaming).
+We define a relation $R'$ relating states of $s_{12}$ and $s_{13}$ as follows:
+\[ R' \mpar{s_{12}, s_{13}} = R\mpar{s_{2}, s_{2}} \wedge \reach{A_{12}}\mpar{s_{12}} \wedge \bigwedge_\subbox{v_1\in V_1}
+ v^1_1=v^2_1\wedge s^1_1 = s^2_1\]
+Let us denote $H'=H\cup J_1 \setminus\{k\}$.
+We want to prove that $\mpar{R', H'}$  is a hole-tracking simulation of $A_{12}$ and $A_{13}$. As for the previous proof we deal with cases:
+\begin{enumerate}
+\item We have to prove that it holds for the initial configurations:
+\[\sigma_{012} \uplus \sigma_{013} \vdash R'\mpar{s_{012}, s_{013}}\]
+with $\sigma_{012} = \sigma_{01}^1 \uplus \sigma_{02}$, $\sigma_{013} = \sigma_{01}^2 \uplus \sigma_{03}$, $s_{012}=(s_{01}^1,s_{02})$, and $s_{013}=(s_{01}^2,s_{03})$.\\
+By using the fact that $R$ relates initial configurations of  $A_2$ and $A_3$, we have  the following statement:
+$\mpar{\sigma_{02} \uplus \sigma_{03} \vdash R\mpar{s_{02}, s_{03}}}$,  and relying on the  fact that initial states are reachable $\sigma_{012} \vdash \reach{A_{12}}\mpar{s_{012}}$ we have 
+\[ \mpar{\sigma_{02} \uplus \sigma_{03} \vdash R\mpar{s_{02}, s_{03}}} \wedge 
+\mpar{\sigma_{012} \vdash \reach{A_{12}}\mpar{s_{012}}}\]
+Because initial valuations $\sigma_{01}^1$ and $\sigma_{01}^2$ associate the same values to the ``same'' variables modulo renaming, we have the tautology:\\ $\left(\,\,{\displaystyle \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge s^1_1 = s^2_1}\right)\psubst{\sigma_{01}^1 \uplus \sigma_{01}^2 }$.
+
+Furthermore, because  the domains of the substitution function are disjoint, the substitution function has an effect only on the related elements,  we get:
+\begin{align*}
+& \mpar{\sigma_{02} \uplus \sigma_{03} \vdash R\mpar{s_{02}, s_{03}}} \wedge 
+\mpar{\sigma_{012} \vdash \reach{A_{12}}\mpar{s_{012}}}\\
+\implies & R\mpar{s_{02}, s_{03}}\psubst{ \sigma_{02} \uplus \sigma_{03}} \wedge \reach{A_{12}}\mpar{s_{012}} \psubst{\sigma_{012}} \land \mpar{ {\displaystyle \bigwedge_\subbox{v_1\in V_1}\,\, v^1_1=v^2_1\wedge s^1_1 = s^2_1}}\psubst{\sigma_{01}^1 \uplus \sigma_{01}^2 }\\
+\implies & \mpar{R\mpar{s_{02}, s_{03}} \wedge \reach{A_{12}}\mpar{s_{012}}  \wedge \bigwedge_\subbox{v_1\in V_1}  v^1_1=v^2_1\wedge s^1_1 = s^2_1} \psubst{ \sigma_{02} \uplus \sigma_{03} \uplus \sigma^1_{01}\uplus \sigma^2_{01} \uplus \sigma_{012}}\\
+\implies & \sigma_{012} \uplus \sigma_{013} \vdash R'\mpar{s_{012}, s_{013}}
+\end{align*}
+
+\item Second, we need to prove for any OT $t_{12}$ in $T_{12}$ originating from $s_{12}$
+
+\begin{align*}
+		&  \OTx{12}{}{12}{12} \in \fOT{s_{12}}
+\end{align*}		
+there exists an indexed family $t_{13x}$ of OTs originating from $s_{13}$ that simulates it: 
+\begin{align*}
+		&  \mpar{\OTx{13}{x}{13x}{13x} \in \fOT{s_{13}}}^{x \in X}
+\end{align*}	
+such that  $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$ and\\
+
+\begin{align*}		
+V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \wedge\\[12pt]
+			 g_{13x} \wedge R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
+		\end{array}} 
+	\end{align*}
+By definition of composition and open automata refinement we have: 
+\begin{align*}
+&V_{12}= V^1_1\uplus V_3 \text{ and }
+V_{13}= V^2_1\uplus V_3\\
+& H'=H_{23}\uplus J_1 \setminus \{k\} \subseteq J_1\uplus \mpar{J_2 \cap J_3} \setminus \{k\} = \mpar{J_1\uplus J_2 \setminus \{k\} } \cap \mpar{J_1\uplus J_3 \setminus \{k\}} = J_{13} \cap J_{13} \\
+\end{align*}
+~\qed
+\end{enumerate}
 

### 2022-03-09 2021-Refinement/paper/refinementarticle.tex
proof thm 3 in progress

@@
 \usepackage{nccrules}
+\usepackage{mathtools}
 \AtBeginDocument{\renewcommand\setminus{\smallsetminus}}
@@
 proving that two implementation are equivalent, or justifying optimisations and transformations, by establishing that the
-behaviors of a modified program simulate those of to the source one.
+behaviours of a modified program simulate those of to the source one.
 
 In this article, we discuss a notion of refinement between so-called "open automata", which are symbolic
-behavioral models for communicating systems. Open automata may have "holes" modeling elements of their
-context, and can be composed by instanciation of the holes. This allows for a compositional approach for
-verification of their behavior, essential to address proofs about large realistic systems.
+behavioural models for communicating systems. Open automata may have "holes" modelling elements of their
+context, and can be composed by instantiation of the holes. This allows for a compositional approach for
+verification of their behaviour, essential to address proofs about large realistic systems.
 
@@
 \appendix
+
 \section{Proof of Transitivity}\label{sec:proof-transitivity}
@@
 \begin{enumerate}
-\item $R_{13}$ satisfies initial configurations.
+\item Firstly, we have to $R_{13}$ satisfies initial configurations:
+\[\sigma_{01} \uplus \sigma_{03} \vdash R_{13} \mpar{s_{01}, s_{03}}\]
 By knowing that substitutions only have an effect on the variables of the open automaton they belong to, they also produce terms containing only variables of the open automaton they belong to.
@@
  \end{align*}
-Since $\sigma_{02}$ has no effect on variables of $s_{01}$ and $s_{03}$ thus we get:
-\[\sigma_{01} \uplus \sigma_{03} \vdash R_{13} \mpar{s_{01}, s_{03}}\]
-\item Consider $\mpar{s_{1}, s_{3}} \in R_{13}$ then there is a set of states $(s_{2p})^{p\in P}$ of $A_2$ relating  $s_{1}$ and $s_{3}$:
+Since $\sigma_{02}$ has no effect on variables of $s_{01}$ and $s_{03}$ thus we get the expected result.
+
+\item Secondly, we need to prove that for any open transition $t_1$ in $T_1$  originating from $s_1$:
+\begin{align*}
+\OTx{1}{}{1}{1} \in \fOT{s_1}
+\end{align*}
+there exists an indexed family of OTs originating from $s_{3}$: 
+\begin{multline*}
+V_1 \uplus  V_3 \uplus \fvars{t_1}
+\vdash\\\hspace{2em}
+\mpar{R_{13}\mpar{s_1, s_3} \wedge g_1 \implies 
+\operatorname*{\bigsymb{\bigvee}}_{z \in Z}
+\mpar{\everymath{\displaystyle}
+\begin{array}{l}
+\alpha_1=\alpha_{3z}\wedge \bigwedge_\subbox{j \in J'_{3z} \cap (H\cap H')} \beta_{1j}=\beta_{3jz} \wedge \\g_{3z}\wedge 
+{R_{12}\mpar{s'_1,s'_{3z}}}\psubst{\psi_1  \uplus \psi_{3z}}
+\end{array}}}
+\end{multline*}	
+\medskip
+ Consider $\mpar{s_{1}, s_{3}} \in R_{13}$ then there is a set of states $(s_{2p})^{p\in P}$ of $A_2$ relating  $s_{1}$ and $s_{3}$:
 \[R_{13}(s_1,s_3)=\bigvee_{{p\in P}
@@
 
-Let's consider any $s_{2p} \in (s_{2p})^{p\in P}$.
-
-On one side, we have for any open transition $t_1$ in $T_1$  originating from $s_1$:
+Let's consider any $s_{2p} \in (s_{2p})^{p\in P}$. We have on one side,  for any open transition $t_1$ in $T_1$  originating from $s_1$:
 \begin{align*}
@@
 \end{align*}
-there exist an indexed family of OTs originating from $s_{2p}$: 
+there exists an indexed family of OTs originating from $s_{2p}$: 
 \begin{align*}
@@
 \end{multline*}		
-
-\begin{multline*}
-%\everymath{\displaystyle}
-\bigforall V_1 \uplus V_2 \uplus \fvars{t_1}\,\,
-\bigexists \mpar{\fvars{\alpha_{1}}  \cup
-\!\!\!
-\bigcup_{j \in J'_{2px} \cap H}\!\!\!\!\!\fvars{\beta_{1j}}} \setminus \mpar{V_1 \uplus V_2 \uplus \fvars{t_1}}, \\ \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X_p} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \nwedge\\
-			 g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}}
-		\end{array}}} \\
-	\end{multline*}	
-\medskip
-Adding to both sides of the implication the predicate $R_{23}\mpar{s_{2p},s_3}$ we get: \footnote{Note for the sake of readability, when we justify each step in a a proof
-we omit to rewrite the quantification over of formula which remains unchanged.}
-\begin{align*}
+Adding to both sides of the implication the predicate $R_{23}\mpar{s_{2p},s_3}$ we get: 
+\begin{multline*}
+V_1 \uplus V_2 \uplus V_3  \uplus \fvars{t_1} \vdash\\
 R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies\hspace{5.5cm}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
@@
 			 g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}} \land R_{23}\mpar{s_{2p},s_3}
-		\end{array}} \qquad (*) \\
-\end{align*}
-
+		\end{array}} \qquad (*) 
+\end{multline*}	
 On the other side, according the relation between $A_2$ and $A_3$ we have for any open transition $t_{2px}$ in $T_2$ originating from $s_{2p}$:
@@
 \begin{multline*}
-\everymath{\displaystyle}
-V_2 \uplus V_3 \uplus \fvars{t_{2px}} \vdash\\\hspace{2em} \mpar{R_{23}\mpar{s_{2p}, s_{3}} \wedge g_{2px} \implies \operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
+%\everymath{\displaystyle}
+V_2 \uplus V_3 \uplus \fvars{t_{2px}} \vdash\\
+R_{23}\mpar{s_{2p}, s_{3}} \wedge g_{2px} \implies \hspace{7cm}\\ \operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
 \begin{array}{l}
@@
 			g_{3pxy} \wedge R_{23}\mpar{s'_{2px}, s'_{3xy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
-		\end{array}}} 
-\end{multline*}
-that can be re-written as follows:
-\begin{multline*}
-\everymath{\displaystyle}
-\bigforall V_2 \uplus V_3 \uplus \fvars{t_{2px}}\,\,\bigexists \mpar{\fvars{\alpha_{2px}} \cup\!\!\!\!\!\! \bigcup_{j \in J'_{3pxy}
-\cap H'}\!\!
-\!\!\!\!\fvars{\beta_{2pxj}}} \setminus \mpar{V_2 \uplus V_3 \uplus \fvars{t_{2px}}},\\ \mpar{R_{23}\mpar{s_{2p}, s_{3}} \wedge g_{2px} \implies \operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			 \alpha_{2px}=\alpha_{3pxy} \wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{2pxj}=\beta_{3pxyj} \nwedge\\
-			 g_{3pxy} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
-		\end{array}}} \qquad (**)
-\end{multline*}
+		\end{array}}  \qquad (**)
+\end{multline*}
+
 The following  can be derived from the two previous cases: \\
@@
 $\forall x \in X, \forall y \in Y,  J'_1 \cap (H \cap H') = J'_{3pxy} \cap (H\cap H')$ \\
-In addition, by replacing the formula $(**)$ in $(*)$, we get: 
-\begin{multline*}
-\everymath{\displaystyle}
-\bigforall V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1}\uplus \fvars{t_{2px}}\\ 
-\bigexists  \mpar{\fvars{\alpha_{1}}  \cup \!\!\!\!\!\!\bigcup_{j \in J'_{2px} \cap H} \!\!\!\!\!\!\!\fvars{\beta_{1j}}  \cup \fvars{\alpha_{2px}}  \cup \!\!\!\!\!\!\bigcup_{j \in J'_{3pxy} \cap H'} \!\!\!\!\!\!\!\fvars{\beta_{2pxj}}}  \setminus \\ \mpar{V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1}\uplus \fvars{t_{2px}}}  \\
+By combining  formula $(**)$ in $(*)$, we get: 
+\begin{multline*}
+V_1 \uplus V_2 \uplus V_3  \uplus \fvars{t_1}\uplus \fvars{t_{2px}} \vdash\\
 R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies \hspace{4.5cm}\\\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
@@
 \begin{multline*}
-\everymath{\displaystyle}
-\bigforall V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1}\uplus \fvars{t_{2px}}\\ \bigexists  \mpar{\fvars{\alpha_{1}}  \cup \!\!\!\!\!\!\bigcup_{j \in J'_{3pxy} \cap (H\cap H')} \!\!\!\!\!\!\!\fvars{\beta_{1j}}  \cup \fvars{\alpha_{2px}}  \cup \!\!\!\!\!\!\bigcup_{j \in J'_{3pxy} \cap (H\cap H')} \!\!\!\!\!\!\!\fvars{\beta_{2pxj}}}  \setminus \hspace{6cm}\\ \mpar{V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1}\uplus \fvars{t_{2px}}}  \\
+V_1 \uplus V_2 \uplus V_3  \uplus \fvars{t_1}\uplus \fvars{t_{2px}}  \vdash\\
 R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies 
@@
 Because of the domain of the substitutions of the relations, we have:
-\begin{align*}
+\begin{multline*}
+V_1 \uplus V_2 \uplus V_3  \uplus \fvars{t_1}\uplus \fvars{t_{2px}} \vdash\\
 R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies 
@@
 \end{array}}
-\end{align*}
-
+\end{multline*}
 This is valid for all $s_{2p} \in (s_{2p})^{p\in P}$.
 We need to rely on the disjunction of all possible paths to relate $s_1$ and $s_3$ with ${\displaystyle R_{13}(s_1,s_3)=\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}}$.
-
-\begin{multline*}
+\begin{multline*}
+V_1 \uplus V_2 \uplus V_3  \uplus \fvars{t_1} \uplus  \biguplus_\subbox{p \in P} \fvars{t_{2px}} \vdash\\
 \operatorname*{\bigsymb{\bigvee}}_{p\in P} \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1} \implies 
@@
 \end{multline*}
-Indeed, we have:
-\begin{multline*}
-R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}} \implies\\ R_{13}\mpar{s'_1,s'_{3pxy}}
-\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}
-\end{multline*}
-Since $\psi_{2px}$ has no effect on variables of $A1$ and $A3$, it then implies:
-\begin{align*}
-R_{13}\mpar{s'_1,s'_{3pxy}}\psubst{\psi_1  \uplus \psi_{3pxy}}
+Since $\psi_{2px}$ has no effect on variables of $A_1$ and $A_3$, it then implies:
+\begin{align*}
+R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}  \\  
+\implies R_{13}\mpar{s'_1,s'_{3pxy}}
+\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}  \\ 
+\implies R_{13}\mpar{s'_1,s'_{3pxy}}\psubst{\psi_1  \uplus \psi_{3pxy}}
 \end{align*}
@@
 \begin{multline*}
-\everymath{\displaystyle}
-\bigforall V_1 \uplus  V_3 \uplus \fvars{t_1}\\
-\bigexists \mpar{\fvars{\alpha_{1}}  \cup\!\!\! \bigcup_{j \in J'_{3z} \cap H \cap H'} \!\!\!\fvars{\beta_{1j} } } \setminus  \mpar{V_1 \uplus  V_3 \uplus \fvars{t_1}}\hspace{3cm}\\
+V_1  \uplus V_3  \uplus \fvars{t_1} \vdash\\
 R_{13}(s_1,s_3)  \wedge g_1 \implies 
@@
 \alpha_1=\alpha_{3z}\wedge \bigwedge_\subbox{j \in J'_{3z} \cap (H\cap H')} \beta_{1j}=\beta_{3jz} \wedge \\g_{3z}\wedge 
-{R_{12}\mpar{s'_1,s'_{3z}}}\psubst{\psi_1  \uplus \psi_{3z}}
+{R_{13}\mpar{s'_1,s'_{3z}}}\psubst{\psi_1  \uplus \psi_{3z}}
 \end{array}}}
@@
 \medskip
-\item Concerning the condition of deadlock reducing. According to the relation between   $A_2$ and $A_3$ we have for all $\mpar{s_{2p}, s_3} \in S_2 \times S_3$:
+\item Finally, the satisfaction of the condition of deadlock reducing. According to the relation between   $A_2$ and $A_3$ we have for all $\mpar{s_{2p}, s_3} \in S_2 \times S_3$:
 \begin{multline*}
@@
 \end{multline*}
-that can be rewritten:
-\begin{multline*}
-\everymath{\displaystyle}
-\bigforall \mpar{V_2\! \uplus\!V_3 \uplus\!\! \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3}}\\
-\bigexists \mpar{\fvars{\alpha_{3}}  \cup \!\!\bigcup_{j \in J'_{3}} \!\!\fvars{\beta_{3j}}} \cup \mpar{\fvars{\alpha_{2px}}  \cup \!\!\! \bigcup_{j \in J'_{2p}} \!\!\!\fvars{\beta_{2pxj}}}
- \setminus \mpar{V_2\! \uplus\!V_3 \uplus\!\! \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3}},\\
-R_{23}\mpar{s_{2p}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} 
-\end{multline*}
 By adding the term $R_{12}\mpar{s_1,s_{2p}}$ to both sides of the implication, we get:
-\begin{align*}
+\begin{multline*}
+V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_{2p}} \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash \\
 R_{12}\mpar{s_1,s_{2p}}\wedge R_{23}\mpar{s_{2p}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies R_{12}\mpar{s_1,s_{2p}}\wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}}
-\end{align*}
+\end{multline*}
 This is valid for all $s_{2p} \in (s_{2p})^{p\in P}$ then we have:
-\begin{align*}
+\begin{multline*}
+V_1 \uplus V_2 \uplus V_3 \uplus \biguplus_\subbox{p \in P} \fvars{t_{2p}} \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash \\
 \operatorname*{\bigsymb{\bigvee}}_{p\in P}\mpar{
 R_{12}\mpar{s_1,s_{2p}}\wedge R_{23}\mpar{s_{2p}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies R_{12}\mpar{s_1,s_{2p}}\wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}}}
-\end{align*}
+\end{multline*}
 This results in:
-\begin{align*}
+\begin{multline*}
+V_1 \uplus V_2 \uplus V_3 \uplus\biguplus_\subbox{p \in P} \fvars{t_{2p}} \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash \\
 R_{13}\mpar{s_1,s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \operatorname*{\bigsymb{\bigvee}}_{p\in P}\mpar{ R_{12}\mpar{s_1,s_{2p}}\wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}}}
-\end{align*}
+\end{multline*}
 Yet according to the relation between $A_1$ and $A_2$ we have  for all $\mpar{s_1, s_{2p}} \in S_1 \times S_2$:
 \begin{multline*}
- V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{2p} \in \fOT{s_{2p}}} \fvars{t_{2p}} \vdash \left(R_{12}\mpar{s_1, s_{2p}} \wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
-\end{multline*}
-This can be rewritten as follows: 
-\begin{multline*}
-\everymath{\displaystyle}
-\bigforall \mpar{V_1\! \uplus\! V_2\! \uplus  \biguplus_\subbox{t_{2p} \in \fOT{s_{2p}}} \fvars{t_{2p}}}\\
-\bigexists \mpar{\fvars{\alpha_{2px}}  \cup  \bigcup_{\begin{array}{c} \subbox{p\in P}\\ \subbox{j \in J'_{2p}}
-\end{array}} \!\! \fvars{\beta_{2pxj}}}\cup \mpar{\fvars{\alpha_{1}}  \cup\!\! \bigcup_{j \in J'_{1}} \!\!\fvars{\beta_{1j}}}
- \setminus \mpar{V_1\! \uplus\! V_2\! \uplus \biguplus_\subbox{t_{2p} \in \fOT{s_{2p}}} \fvars{t_{2p}}},\\
-R_{12}\mpar{s_1, s_{2p}} \wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
-\end{multline*}
+ V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{2p} \in \fOT{s_{2p}}} \fvars{t_{2p}} \vdash R_{12}\mpar{s_1, s_{2p}} \wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
+\end{multline*}
+
 This formula is valid for all $s_{2p} \in (s_{2p})^{p\in P}$,  thus we can state the following:
-\begin{align*}
+\begin{multline*}
+ V_1 \uplus V_2 \uplus \biguplus_{\mathclap{\substack{t_{2p} \in \fOT{s_{2p}}\\ p \in P}}} \fvars{t_{2p}} 
+\vdash \\
 \operatorname*{\bigsymb{\bigvee}}_{p\in P}\mpar{R_{12}\mpar{s_1, s_{2p}} \wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} }  \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
-\end{align*}
-By using transitive property of implication on formula obtained form both relations and by removing the $A_2$ variables that have not effect on   $A_1$ et  $A_3$, we get:
-\begin{multline*}
-\everymath{\displaystyle}
-\bigforall \mpar{V_1\! \uplus\!V_3 \uplus\!\! \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3}}\\
-\bigexists \mpar{\fvars{\alpha_{3}}  \cup \!\!\bigcup_{j \in J'_{3}} \!\!\fvars{\beta_{3j}}} \cup \mpar{\fvars{\alpha_{1}}  \cup\!\! \bigcup_{j \in J'_{1}} \!\!\fvars{\beta_{1j}}}
- \setminus \mpar{V_1\! \uplus\!V_3 \uplus\!\! \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3}},\\
-R_{13}\mpar{s_1,s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3}
-\implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
-\end{multline*}
-This allows us to get the desired result:
+\end{multline*}
+By using transitive property of implication on formula obtained form both relations and by removing the $A_2$ variables that have not effect on   $A_1$ et  $A_3$, we get the desired result:
 \begin{multline*}
@@
 \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
-\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \land \mpar{\bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }\\
+\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \land \mpar{\,\,\bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }\\
 \implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma^1_{03}\uplus \sigma^2_{03}\uplus \sigma_{013} }\\
@@
 \end{align*}
-
 \item Second, we need to prove for any OT $t_{13}$ in $T_{13}$ originating from $s_{13}$:
@@
 \end{align*}
-
-\medskip
-
 We have by hypothesis $\wrel{A_1}{A_2}{H}$, then for any open transition $t_1$ in $T_1$  originating from $s_1$:
@@
 \]
-
 We then obtain a family of OTs by the simulation of $A_1$ by $A_2$ (stated above).
@@
 
-* or by an the transition $t_1=\OTx{1}{}{1}{1}$ alone with the state $s^1_3$ unchanged, if $k \not\in J_1'$
+* or by  the transition $t_1=\OTx{1}{}{1}{1}$ alone with the state $s^1_3$ unchanged, if $k \not\in J_1'$
 \[t_{13} = \OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, s^1_3}}{\alpha_1}{\beta_{1j}^{j \in J'_1}}{g_1}{\psi_1}
@@
 
-\medskip
-
 These two cases define (depending on how $t_{13}$ is built) the family $t_{23x}$ of OTs we are looking for.
@@
 	\end{align*}
-
 For all $x \in X$ we have to consider both  cases:
@@
 & =((J'_{2x}\cap H)\uplus J^{2 \prime}_{3})\setminus \mbrc{k}\text{ since } J^{2 \prime}_{3}\subseteq J_3\\
-& =(J'_1\cap H)\uplus J^{1 \prime}_{3}\setminus \mbrc{k}\quad \text{ since } J^{1 \prime}_{3}=J^{2 \prime}_{3} \text{ and } J'_1 \cap H = J'_{2x} \cap H\\
+& =((J'_1\cap H)\uplus J^{1 \prime}_{3})\setminus \mbrc{k}\quad \text{ since } J^{1 \prime}_{3}=J^{2 \prime}_{3} \text{ and } J'_1 \cap H = J'_{2x} \cap H\\
 &= ((J'_1 \cap H) \uplus (J^{1 \prime}_{3} \cap J_3)) \setminus \mbrc{k}\text{ since } J^{1 \prime}_{3}\subseteq J_3\\ 
@@
 		& = J'_{13} \cap H'\\
-\text{if } k \notin J'_1:\quad &	J'_{23x} \cap H'  = \mpar{J'_{2x} } \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
+\text{if } k \notin J'_1:\quad &	J'_{23x} \cap H'  = J'_{2x}  \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
 & = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
-& = \mpar{J'_1\cap H }\\
-& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'\\
+& = \mpar{J'_1\cap H } \text{ since } J'_1 \cap H = J'_{2x} \cap H\\
+& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'
 \end{align*}
@@
 \end{multline*}
-We use the the first, we extend the valuation to cover the variables of  $t^2_3$ in $t_{23}$ using their value in $t_3$ and because $\fvars{t_{13}} \vdash \reach{A_{13}}\mpar{s_{13}}$, we get"
+We use the the first, we extend the valuation to cover the variables of  $t^2_3$ in $t_{23}$ using their value in $t_3$ and because $\fvars{t_{13}} \vdash \reach{A_{13}}\mpar{s_{13}}$, we get:
 \begin{multline*}
@@
 
-We denote $A_1=  \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}$ and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and $A_3 = \OA{S_3}{s_{03}}{J_3}{V_3}{\sigma_{03}}{T_3}$.
+We denote $A_1=  \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}$ and \(A_2 = \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and $A_3 = \OA{S_3}{s_{03}}{J_3}{V_3}{\sigma_{03}}{T_3}$.
 
@@
 By using the fact that $R$ relates initial configurations of  $A_2$ and $A_3$, we have  the following statement:
-$\mpar{\sigma_{02} \uplus \sigma_{03} \vdash R\mpar{s_{02}, s_{03}}}$,  and relying on the  fact that initial states are reachable $\sigma_{012} \vdash \reach{A_{12}}\mpar{s_{012}}$ we have 
+$\mpar{\sigma_{02} \uplus \sigma_{03} \vdash R\mpar{s_{02}, s_{03}}}$,  and relying on the  fact that initial states are reachable $\sigma_{012} \vdash \reach{A_{12}}\mpar{s_{012}}$ we have:
 \[ \mpar{\sigma_{02} \uplus \sigma_{03} \vdash R\mpar{s_{02}, s_{03}}} \wedge 
@@
 \mpar{\sigma_{012} \vdash \reach{A_{12}}\mpar{s_{012}}}\\
-\implies & R\mpar{s_{02}, s_{03}}\psubst{ \sigma_{02} \uplus \sigma_{03}} \wedge \reach{A_{12}}\mpar{s_{012}} \psubst{\sigma_{012}} \land \mpar{ {\displaystyle \bigwedge_\subbox{v_1\in V_1}\,\, v^1_1=v^2_1\wedge s^1_1 = s^2_1}}\psubst{\sigma_{01}^1 \uplus \sigma_{01}^2 }\\
+\implies & R\mpar{s_{02}, s_{03}}\psubst{ \sigma_{02} \uplus \sigma_{03}} \wedge \reach{A_{12}}\mpar{s_{012}} \psubst{\sigma_{012}} \land \mpar{\,\, {\displaystyle \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge s^1_1 = s^2_1}}\psubst{\sigma_{01}^1 \uplus \sigma_{01}^2 }\\
 \implies & \mpar{R\mpar{s_{02}, s_{03}} \wedge \reach{A_{12}}\mpar{s_{012}}  \wedge \bigwedge_\subbox{v_1\in V_1}  v^1_1=v^2_1\wedge s^1_1 = s^2_1} \psubst{ \sigma_{02} \uplus \sigma_{03} \uplus \sigma^1_{01}\uplus \sigma^2_{01} \uplus \sigma_{012}}\\
@@
 \end{align*}	
-such that  $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$ and\\
-
-\begin{align*}		
+such that  $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$ and
+\begin{multline*}	
 V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
@@
 		\end{array}} 
-	\end{align*}
+	\end{multline*}
 By definition of composition and open automata refinement we have: 
@@
 V_{13}= V^2_1\uplus V_3\\
-& H'=H_{23}\uplus J_1 \setminus \{k\} \subseteq J_1\uplus \mpar{J_2 \cap J_3} \setminus \{k\} = \mpar{J_1\uplus J_2 \setminus \{k\} } \cap \mpar{J_1\uplus J_3 \setminus \{k\}} = J_{13} \cap J_{13} \\
-\end{align*}
+& H'=H_{23}\uplus J_1 \setminus \{k\} \subseteq J_1\uplus \mpar{J_2 \cap J_3} \setminus \{k\} = \mpar{J^1_1\uplus J_2 \setminus \{k\} } \cap \mpar{J^2_1\uplus J_3 \setminus \{k\}} = J_{12 } \cap J_{13} \\
+\end{align*}
+We have by hypothesis $\wrel{A_2}{A_3}{H}$, then for any open transition $t_2$ in $T_2$  originating from $s_2$:
+\begin{align*}
+\OTx{2}{}{2}{2} \in \fOT{s_2}
+\end{align*}
+there exists an indexed family of OTs originating from $s_{2}$: 
+\begin{align*}
+\mpar{\OTx{3}{x}{3x}{3x} \in \fOT{s_{3}}}^{x \in X} 
+\end{align*}
+such that $\forall x \in X, J'_{3x} \cap H = J'_2 \cap H$ and
+\begin{multline*}
+%\everymath{\displaystyle}
+V_2 \uplus V_3 \uplus \fvars{t_2} \vdash\\ \mpar{R\mpar{s_2, s_3} \wedge g_2 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_2 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj} \nwedge\\
+			 g_{3x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
+		\end{array}}}  \qquad \quad (*)
+\end{multline*}	
+\smallskip
+Consider any transition $t_{12}$ in $A_{12}$,  $t_{12}$ is obtained (by case analysis on the definition of composition)
+
+* either by the composition of a transition $t_2=\OTx{2}{}{2}{2}$ and a transition \[t_1^1=
+\OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{   {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1} \qquad \text{ when } k \in {J^1_{1}}^{\prime}
+\]. We obtain:
+%%%% Attention deactiver ici
+\[
+t_{12} = \OT{\mpar{s^1_1, s_2}}{\mpar{{s^1_1}',s'_2 }}{\alpha^1_1}{{\beta^1_{1j}}^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {(\beta_{2j})^{j \in J^{\prime}_2} }}{g^1_1 \wedge g_2 \wedge \alpha_2 = \beta^1_{1k}}{\psi^1_1 \uplus \psi_2} \qquad \text{ where } k \in {J^1_{1}}^{\prime}
+\]
+
+We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (stated above).
+By hypothesis we have $k \in H$, so in the case where $k \in {J^1_{1}}^{\prime}$, we deduce that $k \in J'_{3x}$ we can  then build  a family of OTs $t_{13x}^{x\in X}$ with the same transitions of $A_1$ (up to renaming) as those used to build $t_{12}$.
+\[
+t_{13x} = \left(\OT{\mpar{s^2_1, s_3}}{\mpar{{s^2_{1}}',s'_{3x}}}{\alpha^2_{1}}  {{(\beta^2_{1j})^{j \in J^{2 \prime}_1}}\uplus \beta_{3xj}^{j \in J'_{3x}  \setminus \{k\}} }{g_{3x} \wedge g^2_1 \wedge \alpha^2_1 = \beta_{3xk}}{\psi_{3x} \uplus \psi^2_1}
+\right)^{x\in X}\]
+Recall that in this case  $k \in {J^1_{1}}^{\prime}$
+
+* or by an the transition $t_1^2=
+\OT{ s^2_1}{{s^2_1}'}{\alpha_1^2}{{(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{ g^2_1 }{ \psi^2_1}$  alone with the state $s_2$ unchanged, if $k \not\in {J^1_{1}}^{\prime}$
+\[t_{12} = \OT{\mpar{s^2_1, s_2}}{\mpar{{s^2_1}', s'_2}}{\alpha_1^2}{ {(\beta^2_{1j})^{j \in J^{1 \prime}_1} }}{g^2_1}{\psi^2_1}
+\]
+We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (stated above).
+As  $k \in H$ we have $k \not\in J'_{3x}$ and we build:
+\[t_{13x} = \left(
+\OT{\mpar{s^1_1, s_3}}{\mpar{s^2_1,s'_{2x}}}{\alpha_{3x}}{\beta_{3xj}^{j \in J'_{3x}}}{g_{3x}}{\psi_{3x}} \right)^{x\in X}\]
+
+According to how the transition $t_{12}$ is built we have to consider both cases to prove the following:
+ $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$ and
+\begin{multline*}	
+V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \wedge\\[12pt]
+			 g_{13x} \wedge R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
+		\end{array}} 
+	\end{multline*}
+For all $x \in X$ we have to consider both  cases:
+\begin{align*}
+	\text{if } k \in {J^1_{1}}^{\prime}:\quad &  J'_{13} \cap H'  
+=((J^{2 \prime}_{1} \uplus J'_{3x}) \setminus \mbrc{k}) \cap ((H\uplus J_1) \setminus\{k\} )\\
+& =((J^{2 \prime}_{1} \cap (H\uplus J_1)) \uplus (J'_{3x} \cap  (H\uplus J_1)))\setminus \mbrc{k}\\
+& =((J^{2 \prime}_{1} \cap  J_1)) \uplus (J'_{3x} \cap H))\setminus \mbrc{k}\text{ since }  J^{2 \prime}_{1}\cap H = \emptyset \text{ and } J'_{3x}\cap J_1 = \emptyset  \\
+& =(J^{2 \prime}_{1} \uplus (J'_{3x} \cap H))\setminus \mbrc{k} \text{ since } J^{1 \prime}_{1}\subseteq J_1\\
+& =(J^{1 \prime}_{1} \uplus (J'_{2} \cap H))\setminus \mbrc{k}  \text{ since } J^{1 \prime}_{1}=J^{2 \prime}_{1} \text{ and } J'_2 \cap H = J'_{3x} \cap H\\
+&  =((J^{1 \prime}_{1} \cap J_{1}) \uplus (J'_{2} \cap H))\setminus \mbrc{k} \text{ since } J^{1 \prime}_{1} \subseteq J_1 \\
+& = (J'_{2} \cap (J_1 \uplus H)) \uplus (J^{1 \prime}_{1}\cap (J_1 \uplus H))\setminus \mbrc{k} \text{ since } 
+J_1 \cap  J'_{2}= \emptyset \text{ and } H \cap J^{1 \prime}_{1} = \emptyset\\
+& = ((J'_{2} \uplus J^{1 \prime}_{1})\setminus \mbrc{k}) \cap   ((J_1 \uplus H)\setminus \mbrc{k})\\
+& = J'_{12}\cap H'\\
+\text{if } k \notin {J^1_{1}}^{\prime}:\quad &	J'_{13x} \cap H'  = J'_{3x}  \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \\
+& = \mpar{J'_{3x}\cap H } \text{ since } J'_{3x}\cap J_1=\emptyset \land k\not\in J'_{3x} \\
+& = \mpar{J'_2\cap H } \text{ since } J'_2 \cap H = J'_{3x} \cap H\\
+& = \mpar{J'_{12}\cap H' } \text{ since } J_2\cap J'_1=\emptyset \land k\not\in {J^1_{1}}^{\prime}
+\end{align*}
+For the rest of the formula we will also consider the two cases separately. 
+\begin{itemize}
+\item if $k \in {J^1_{1}}^{\prime}$:\\
+As before, the proof  is based  on the fact that the composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.
+By construction of  $t_{12}$ and $t_{13}$ we have $\alpha_{12}=
+\alpha^1_{1}$ and $\alpha_{13x}=\alpha^2_{1}$, so we deduce: 
+$\alpha_{12} = \alpha_{13x}$. In addition we have:\\
+ $\beta_{12j}^{j\in J'_{12}}= {{\beta^1_{1j}}^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {(\beta_{2j})^{j \in J^{\prime}_2} }}$ and $\beta_{13xj}^{j\in J'_{13}}= {{(\beta^2_{1j})^{j \in J^{2 \prime}_1}}\uplus \beta_{3xj}^{j \in J'_{3x}  \setminus \{k\}} }$\\
+
+Therefore, we have for all $j\in J'_{12}$ (recall that $J'_{12}=J'_{13}$):  \[\beta_{12j} = \beta_{13xj} \Rightarrow (j\in J^{1 \prime}_1 \land \beta^1_{1j}= \beta^2_{1j}) \vee  (j\in J_2 \land \beta_{2j} = \beta_{3xj})  \]\\
+Third, considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up to renaming)  we have: 
+${\displaystyle V^1_{1} \uplus V^2_{1} \uplus \fvars{t_{12}} \vdash \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1\implies \bigwedge_\subbox{j \in J^{\prime}_1} \beta^1_{1j}= \beta^2_{1j}}$
+\end{itemize}
+
 ~\qed

### 2022-03-10 2021-Refinement/paper/refinementarticle.tex
correction + avancement preuve thm 3

@@
 \usepackage{tikz,mathpartir}
-
+\usepackage{mathtools}
 \usepackage{amsmath,amssymb,mathabx}
-%\usepackage{amsthm}
 %\usepackage{unicode-math}
@@
 \usepackage{nccrules}
-\usepackage{mathtools}
+
 \AtBeginDocument{\renewcommand\setminus{\smallsetminus}}
@@
 Since $\psi_{2px}$ has no effect on variables of $A_1$ and $A_3$, it then implies:
+
 \begin{align*}
@@
 
-Considering that initial valuations $\sigma_{03}^1$ and $\sigma_{03}^2$ associate the same values to the ``same'' variables modulo renaming, we have the tautology:\\ $\left(\,\,{\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }$.
+Considering that initial valuations $\sigma_{03}^1$ and $\sigma_{03}^2$ associate the same values to the ``same'' variables modulo renaming, so the following holds:\\ $\left(\,\,{\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }$.
 
@@
 Let us denote with $t^2$ and $t^3$  the elements of $A_2$ and $A_3$ respectively.
-Consider any two states $s_{12} = \mpar{s_1,s^1_2}$ and $s_{13} = \mpar{s^2_1,s_3}$ ($s^1_1$ and $s^2_1$  are the same with renaming).
+Consider any two states $s_{12} = \mpar{s^1_1,s_2}$ and $s_{13} = \mpar{s^2_1,s_3}$ ($s^1_1$ and $s^2_1$  are the same with renaming).
 We define a relation $R'$ relating states of $s_{12}$ and $s_{13}$ as follows:
@@
 \mpar{\sigma_{012} \vdash \reach{A_{12}}\mpar{s_{012}}}\]
-Because initial valuations $\sigma_{01}^1$ and $\sigma_{01}^2$ associate the same values to the ``same'' variables modulo renaming, we have the tautology:\\ $\left(\,\,{\displaystyle \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge s^1_1 = s^2_1}\right)\psubst{\sigma_{01}^1 \uplus \sigma_{01}^2 }$.
+Because initial valuations $\sigma_{01}^1$ and $\sigma_{01}^2$ associate the same values to the ``same'' variables modulo renaming, so the following holds:\\ $\left(\,\,{\displaystyle \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge s^1_1 = s^2_1}\right)\psubst{\sigma_{01}^1 \uplus \sigma_{01}^2 }$.
 
@@
 \begin{align*}
-&V_{12}= V^1_1\uplus V_3 \text{ and }
+&V_{12}= V^1_1\uplus V_2 \text{ and }
 V_{13}= V^2_1\uplus V_3\\
@@
 \[
-t_{13x} = \left(\OT{\mpar{s^2_1, s_3}}{\mpar{{s^2_{1}}',s'_{3x}}}{\alpha^2_{1}}  {{(\beta^2_{1j})^{j \in J^{2 \prime}_1}}\uplus \beta_{3xj}^{j \in J'_{3x}  \setminus \{k\}} }{g_{3x} \wedge g^2_1 \wedge \alpha^2_1 = \beta_{3xk}}{\psi_{3x} \uplus \psi^2_1}
+t_{13x} = \left(\OT{\mpar{s^2_1, s_3}}{\mpar{{s^2_{1}}',s'_{3x}}}{\alpha^2_{1}}  {{(\beta^2_{1j})^{{j \in J^{2 \prime}_1} \setminus \{k\}}}\uplus \beta_{3xj}^{j \in J'_{3x}  } }{ g^2_1 \wedge  g_{3x}  \wedge \alpha_{3x} =  \beta^2_{1k}}{\psi_{3x} \uplus \psi^2_1}
 \right)^{x\in X}\]
@@
 
-* or by an the transition $t_1^2=
-\OT{ s^2_1}{{s^2_1}'}{\alpha_1^2}{{(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{ g^2_1 }{ \psi^2_1}$  alone with the state $s_2$ unchanged, if $k \not\in {J^1_{1}}^{\prime}$
-\[t_{12} = \OT{\mpar{s^2_1, s_2}}{\mpar{{s^2_1}', s'_2}}{\alpha_1^2}{ {(\beta^2_{1j})^{j \in J^{1 \prime}_1} }}{g^2_1}{\psi^2_1}
+* or by an the transition $t_1^1=
+\OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{{(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1}$  alone with the state $s_2$ unchanged, if $k \not\in {J^1_{1}}^{\prime}$
+\[t_{12} = \OT{\mpar{s^1_1, s_2}}{\mpar{{s^1_1}', s_2}}{\alpha_1^1}{ {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{g^1_1}{\psi^1_1}
 \]
 We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (stated above).
-As  $k \in H$ we have $k \not\in J'_{3x}$ and we build:
-\[t_{13x} = \left(
-\OT{\mpar{s^1_1, s_3}}{\mpar{s^2_1,s'_{2x}}}{\alpha_{3x}}{\beta_{3xj}^{j \in J'_{3x}}}{g_{3x}}{\psi_{3x}} \right)^{x\in X}\]
+As  $k \in H$ we have $k \not\in J'_{3x}$ and we build with the same transitions of $A_1$ (up renaming):
+\[t_{13x} = \left(\OT{\mpar{s^2_1, s_3}}{\mpar{{s^2_1}', s_{3}}}{\alpha_1^2}{ {(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{g^2_1}{\psi^2_1} \right)^{x\in X}\]
 
@@
 By construction of  $t_{12}$ and $t_{13}$ we have $\alpha_{12}=
-\alpha^1_{1}$ and $\alpha_{13x}=\alpha^2_{1}$, so we deduce: 
+\alpha^1_{1}$ and $\alpha_{13x}=\alpha^2_{1}$. As  $\alpha^1_{1}=\alpha^2_{1}$  we deduce: 
 $\alpha_{12} = \alpha_{13x}$. In addition we have:\\
- $\beta_{12j}^{j\in J'_{12}}= {{\beta^1_{1j}}^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {(\beta_{2j})^{j \in J^{\prime}_2} }}$ and $\beta_{13xj}^{j\in J'_{13}}= {{(\beta^2_{1j})^{j \in J^{2 \prime}_1}}\uplus \beta_{3xj}^{j \in J'_{3x}  \setminus \{k\}} }$\\
-
-Therefore, we have for all $j\in J'_{12}$ (recall that $J'_{12}=J'_{13}$):  \[\beta_{12j} = \beta_{13xj} \Rightarrow (j\in J^{1 \prime}_1 \land \beta^1_{1j}= \beta^2_{1j}) \vee  (j\in J_2 \land \beta_{2j} = \beta_{3xj})  \]\\
-Third, considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up to renaming)  we have: 
-${\displaystyle V^1_{1} \uplus V^2_{1} \uplus \fvars{t_{12}} \vdash \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1\implies \bigwedge_\subbox{j \in J^{\prime}_1} \beta^1_{1j}= \beta^2_{1j}}$
+ $\beta_{12j}^{j\in J'_{12}}= {({\beta^1_{1j}})^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {\beta_{2j}^{j \in J^{\prime}_2} }}$ and $\beta_{13xj}^{j\in J'_{13}}= {{(\beta^2_{1j})^{j \in {J^{2 \prime}_1} \setminus \{k\}}}\uplus \beta_{3xj}^{j \in J'_{3x} } }$\\
+
+Therefore, we have for all $j\in J'_{12}$ (recall that $J'_{12}=J'_{13}$):  \[\beta_{12j} = \beta_{13xj} \Rightarrow (j\in J^{1 \prime}_1 \land \beta^1_{1j}= \beta^2_{1j}) \vee  (j\in J'_2 \land \beta_{2j} = \beta_{3xj})  \]\\
+Third, considering $\beta^1_{1j}$ and  $\beta^2_{1j}$  are the same (up to renaming)  we have: 
+${\displaystyle V^1_{1} \uplus V^2_{1} \uplus \fvars{t_{1}} \vdash \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1\implies \bigwedge_\subbox{j \in J^{\prime}_1} \beta^1_{1j}= \beta^2_{1j}}$.
+
+Suppose that  $V_{2} \uplus V_{3} \uplus \fvars{t_{3x}}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj}}$ holds then we can deduce:
+\begin{align*}
+V^1_{1} \uplus V^2_{1} \uplus V_{2} \uplus V_{3} \uplus \fvars{t_{13x}}
+\vdash &   \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1\implies \bigwedge_\subbox{j \in J^{\prime}_1} \beta^1_{1j}= \beta^2_{1j} \vee  
+\bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj}\\
+\Rightarrow  V_{12} \uplus V_{13}  \uplus \fvars{t_{13x}}\vdash & 
+\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1
+\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{3x}   \cap H)\uplus J^{1 \prime}_1 } \beta_{12j} = \beta_{13xj}} \\  
+\Rightarrow   V_{12} \uplus V_{13}  \uplus \fvars{t_{13x}} \vdash & 
+\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1
+\implies 
+{\displaystyle \bigwedge_\subbox{j \in ((J'_{3x}   \cap H)\uplus J^{1 \prime}_1)\setminus \{k\} } \beta_{12j} = \beta_{13xj}}\\
+\Rightarrow  V_{12} \uplus V_{13}  \uplus \fvars{t_{13x}} \vdash & 
+\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1
+\implies 
+{\displaystyle \bigwedge_\subbox{j \in (J'_{13x}   \cap H')} \beta_{12j} = \beta_{13xj}}
+\end{align*}
+Moreover, from the composition we deduce:
+$g_{12} \Leftrightarrow g^1_1 \wedge g_2 \wedge \alpha_2=\beta^1_{1k}$ and $g_{13x}  \Leftrightarrow g^2_1 \wedge  g_{3x}  \wedge \alpha_{3x}=\beta^2_{1k}$. 
+Furthermore, as    
+$\beta^1_{1k} = \beta^2_{1k}$ then we  deduce:
+$ g^1_1  \wedge \alpha_2=\beta^1_{1k}  \Leftrightarrow g^2_1  \wedge \alpha_{3x}=\beta^2_{1k}$.
+
+By entering all the intermediate results  into the formula $(*)$ we get:
+\begin{multline*}
+%\everymath{\displaystyle}
+V_2 \uplus V_3 \uplus \fvars{t_2} \vdash\\ R\mpar{s_2, s_3} \wedge g_2 \wedge  \mpar{g^1_1  \wedge \alpha_2=\beta^1_{1k}} \wedge \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1
+\implies\hspace{5em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge\\
+			 g_{3x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
+		\end{array}} \wedge    \mpar{g^2_1  \wedge \alpha_{3x}=\beta^2_{1k}}
+\end{multline*}	
+which can be simplified as follows:
+\begin{multline*}
+%\everymath{\displaystyle}
+V_{12} \uplus V_{13} \uplus \fvars{t_{13x}} \vdash\\ R\mpar{s_2, s_3} \wedge g_{12} \wedge \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1
+\implies\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge\\
+			 g_{13x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
+		\end{array}} 
+\end{multline*}
+
 \end{itemize}

### 2022-03-11 2021-Refinement/paper/refinementarticle.tex
proof thm3 in progress

@@
 \end{multline*}
-And finally By hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
+And finally by hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
 \[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
@@
 $\alpha_{12} = \alpha_{13x}$. In addition we have:\\
- $\beta_{12j}^{j\in J'_{12}}= {({\beta^1_{1j}})^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {\beta_{2j}^{j \in J^{\prime}_2} }}$ and $\beta_{13xj}^{j\in J'_{13}}= {{(\beta^2_{1j})^{j \in {J^{2 \prime}_1} \setminus \{k\}}}\uplus \beta_{3xj}^{j \in J'_{3x} } }$\\
-
-Therefore, we have for all $j\in J'_{12}$ (recall that $J'_{12}=J'_{13}$):  \[\beta_{12j} = \beta_{13xj} \Rightarrow (j\in J^{1 \prime}_1 \land \beta^1_{1j}= \beta^2_{1j}) \vee  (j\in J'_2 \land \beta_{2j} = \beta_{3xj})  \]\\
+ $\beta_{12j}^{j\in J'_{12}}= {({\beta^1_{1j}})^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {\beta_{2j}^{j \in J^{\prime}_2} }}$ and $\beta_{13xj}^{j\in J'_{13}}= {{(\beta^2_{1j})^{j \in {J^{2 \prime}_1} \setminus \{k\}}}\uplus \beta_{3xj}^{j \in J'_{3x} } }$
+
+Therefore, we have for all $j\in J'_{12}$ (recall that $J'_{12}=J'_{13}$):  
+\[\beta_{12j} = \beta_{13xj} \Rightarrow (j\in J^{1 \prime}_1 \land \beta^1_{1j}= \beta^2_{1j}) \vee  (j\in J'_2 \land \beta_{2j} = \beta_{3xj})  \]
 Third, considering $\beta^1_{1j}$ and  $\beta^2_{1j}$  are the same (up to renaming)  we have: 
@@
 \end{multline*}	
-which can be simplified as follows:
+which can be simplified and rewritten as follows:
 \begin{multline*}
@@
 \end{multline*}	
+For any transition $t_1$ in $A_1$ relying $s_1$ and $s^{\prime}_1$ and for each $x \in X$ we have:
+\begin{multline*}
+V_{12} \uplus V_{13}  \uplus \fvars{t_{13x}} \vdash\\
+\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1  \wedge s^1_1 = s^2_1 \implies \bigwedge_\subbox{v_1\in V_1}\!\! \mpar{v^1_1=v^2_1} \psubst{\psi_{13x}} \wedge s^{1\prime}_1 = s^{2\prime}_1 
+ \end{multline*}	
+We can deduce for all  $x \in X$ the following statement:
+\begin{multline*}
+V_{12} \uplus V_{13}  \uplus \fvars{t_{13x}} \vdash\\
+\bigwedge_\subbox{v_1\in V_1}\!\!
+v^1_1=v^2_1  \wedge s^1_1 = s^2_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\,\,\everymath{\displaystyle}\bigwedge_\subbox{v_1\in V_1}\!\!
+\mpar{v^1_1=v^2_1} \psubst{\psi_{13x}} \wedge s^{1\prime}_1 = s^{2\prime}_1 }
+ \end{multline*}	
+Therefore, we get:
+\begin{multline*}
+%\everymath{\displaystyle}
+V_{12} \uplus V_{13} \uplus \fvars{t_{13x}} \vdash\\ R\mpar{s_2, s_3} \wedge g_{12} \wedge \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1 \wedge s^1_1 = s^2_1
+\implies \hspace{7em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge\\
+			 g_{13x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}} \wedge\bigwedge_\subbox{v_1\in V_1}\!\! \mpar{v^1_1=v^2_1} \psubst{\psi_{13x}} \wedge s^{1\prime}_1 = s^{2\prime}_1
+		\end{array}   } 
+		\end{multline*}
+
+Considering the hypothesis that 	\(A_1\subst{A_2}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have  for all $t_{12} \in T_{12}$:
+\[ \fvars{t_{12}} \vdash \left(\reach{A_{12}}\mpar{s_{12}} \wedge g_{12} \implies \reach{A_{12}}\mpar{s_{12}'}\psubst{\psi_{12}}\right) \]
+
+\begin{multline*}	
+V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \wedge\\[12pt]
+			 g_{13x} \wedge R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
+		\end{array}} 
+	\end{multline*}
 

### 2022-03-14 2021-Refinement/paper/refinementarticle.tex
proof...

@@
 Overall, we have a family of open transitions $t^{p\in P,x\in X,y\in Y}_{pxy} \subseteq T_3$ that should simulate $t_1$.
-All  combinations of elements in $P$, $X$, and $Y$ provide a set $Z$ of weak open transitions.
-This allows us to get the desired conclusion, that there is a set of weak open transitions indexed over $Z$:
+All  combinations of elements in $P$, $X$, and $Y$ provide a set $Z$ of  open transitions.
+This allows us to get the desired conclusion, that there is a set of  open transitions indexed over $Z$:
 %This provides the desired conclusion:\\
@@
 \medskip
-\item Finally, the satisfaction of the condition of deadlock reducing. According to the relation between   $A_2$ and $A_3$ we have for all $\mpar{s_{2p}, s_3} \in S_2 \times S_3$:
+\item Finally, the satisfaction of the  deadlock reducing condition. According to the refinement relation relating   $A_2$ and $A_3$ we have for all $\mpar{s_{2p}, s_3} \in S_2 \times S_3$:
 \begin{multline*}
@@
 
-Considering the hypothesis that 	\(A_1\subst{A_2}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have  for all $t_{12} \in T_{12}$:
+From the hypothesis, we have \(A_1\subst{A_2}{k}\) is non-blocking.  Then   Definition \ref{Def:Reach} we have  for all $t_{12} \in T_{12}$:
 \[ \fvars{t_{12}} \vdash \left(\reach{A_{12}}\mpar{s_{12}} \wedge g_{12} \implies \reach{A_{12}}\mpar{s_{12}'}\psubst{\psi_{12}}\right) \]	
-
+With the conjunction of the  formula obtained above and after simplifying, we get:
 \begin{multline*}	
@@
 	\end{multline*}
+\item It remains to prove the  satisfaction of the  deadlock reducing condition. According to the relation between   $A_2$ and $A_3$ we have for all $\mpar{s_{2p}, s_3} \in S_2 \times S_3$:
+\begin{multline*}
+ V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash \left(R_{23}\mpar{s_{2p}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} \right)
+\end{multline*}
+By adding the term $R_{12}\mpar{s_1,s_{2p}}$ to both sides of the implication, we get:
 

### 2022-03-22 2021-Refinement/paper/refinementarticle.tex
proof teminee

@@
 
-\begin{definition}[Non-blocking composition]
+\begin{definition}[Non-blocking composition]\label{Def:Non-blockcomp}
 Let \(A_i = \OAg[i]\) with \( 0 \leq i \leq n\) be a family of open automata.
@@
 
-The following  can be derived from the two previous cases: \\
+From the  two previous cases: 
 $\forall x \in X, J'_{2px} \cap H = J'_1 \cap H$ and
-$\forall y \in Y, J'_{2px} \cap H' = J'_{3pxy} \cap H'$ leading to the conclusion:\\
+$\forall y \in Y, J'_{2px} \cap H' = J'_{3pxy} \cap H'$ we conclude:
 $\forall x \in X, \forall y \in Y,  J'_1 \cap (H \cap H') = J'_{3pxy} \cap (H\cap H')$ \\
-By combining  formula $(**)$ in $(*)$, we get: 
+
+In addition, by combining  formula $(**)$ and $(*)$, we get: 
 \begin{multline*}
@@
 \end{multline*}		
-With the restriction of the domain and the rearrangement of the formula, we get:
+With  the rearrangement of the formula, we get:
 \begin{multline*}
@@
 
-Because of the domain of the substitutions of the relations, we have:
+Because of the domain of the substitutions of the relations, the formula can be re-written:
 \begin{multline*}
@@
 \end{multline*}
-This is valid for all $s_{2p} \in (s_{2p})^{p\in P}$.
-We need to rely on the disjunction of all possible paths to relate $s_1$ and $s_3$ with ${\displaystyle R_{13}(s_1,s_3)=\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}}$.
+The formula is valid for all $s_{2p} \in (s_{2p})^{p\in P}$.
+To build $R_{13}$ we need to rely on the disjunction of all possible paths to relate $s_1$ and $s_3$, which leads to\\ ${\displaystyle R_{13}(s_1,s_3)=\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}}$.
 \begin{multline*}
@@
 \end{multline*}
-Since $\psi_{2px}$ has no effect on variables of $A_1$ and $A_3$, it then implies:
-
+Indeed, since $\psi_{2px}$ has no effect on variables of $A_1$ and $A_3$ we have:
 \begin{align*}
@@
 \medskip
-\item Finally, the satisfaction of the  deadlock reducing condition. According to the refinement relation relating   $A_2$ and $A_3$ we have for all $\mpar{s_{2p}, s_3} \in S_2 \times S_3$:
+\item Finally, we need to prove the satisfaction of the  deadlock reducing condition.
+According to the refinement relation relating   $A_2$ and $A_3$ we have for all $\mpar{s_{2p}, s_3} \in S_2 \times S_3$:
 \begin{multline*}
@@
 By using the fact that $R$ relates initial configurations of  $A_1$ and $A_2$, we have  the following statement:
-$\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}}$,  and relying on the  fact that initial states are reachable $\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ we have 
+$\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}}$,  and based on the  fact that initial states are reachable $\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ we have 
 \[ \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
@@
 
-Because  the domains of the substitution function are disjoint, the substitution function has an effect only on the related elements,  we get:
+Additionally, because  the domains of the substitution function are disjoint, the substitution function has an effect only on the related elements,  we get:
 \begin{align*}
@@
 \end{align*}		
-there exists an indexed family $t_{23x}$ of OTs originating from $s_{23}$ that simulates it: 
+there exists an indexed family $t_{23x}$ of OTs originating from $s_{23}$ that simulate it: 
 \begin{align*}
@@
 	\end{align*}
-By definition of composition and open automata refinement we have: 
+Recall that by definition of composition and open automata refinement we have: 
 \begin{align*}
@@
 \end{align*}
-We have by hypothesis $\wrel{A_1}{A_2}{H}$, then for any open transition $t_1$ in $T_1$  originating from $s_1$:
+First of all, we have by hypothesis $\wrel{A_1}{A_2}{H}$, then for any open transition $t_1$ in $T_1$  originating from $s_1$:
 \begin{align*}
@@
 Consider any transition $t_{13}$ in $A_{13}$,  $t_{13}$ is obtained (by case analysis on the definition of composition) 
-
-* either by the composition of a transition $t_1=\OTx{1}{}{1}{1}$ and a transition \[t_3^1=
+\begin{enumerate}
+\item either by the composition of a transition $t_1=\OTx{1}{}{1}{1}$ and a transition \[t_3^1=
 \OT{ s^1_3}{{s^1_3}'}{\alpha_3^1}{   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{ g^1_3 }{ \psi^1_3} \qquad \text{ when } k \in J'_{1} 
@@
 Recall that in this case  $k \in J'_{1}$
-
-* or by  the transition $t_1=\OTx{1}{}{1}{1}$ alone with the state $s^1_3$ unchanged, if $k \not\in J_1'$
+\item  or by  the transition $t_1=\OTx{1}{}{1}{1}$ alone with the state $s^1_3$ unchanged, if $k \not\in J_1'$
 \[t_{13} = \OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, s^1_3}}{\alpha_1}{\beta_{1j}^{j \in J'_1}}{g_1}{\psi_1}
@@
 \OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, s^2_3}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x}}}{g_{2x}}{\psi_{2x}} \right)^{x\in X}\]
+
+\end{enumerate}
 
@@
 \item if $k \in J'_1$:\\
-The proof is based on the following facts.
-First, because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.
+The proof is based on the following facts: (i) Because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.
 By construction of  $t_{13}$ and $t_{23}$ we have $\alpha_{13}=
 \alpha_{1}$ and $\alpha_{23x}=\alpha_{2x}$. So we deduce: 
-$\alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$.\\
-Second, we have: \\ $\beta_{13j}^{j\in J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
+$\alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$.
+(ii) We have: \\ $\beta_{13j}^{j\in J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
 and $\beta_{23xj}^{j\in J'_{23}}= \beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }$\\
-Therefore, we have for all $j\in J'_{13}$ (recall that $J'_{13}=J'_{23}$):  \[\beta_{13j} = \beta_{23xj} \Rightarrow (j\in J_1 \land \beta_{1j} = \beta_{2xj}) \vee (j\in J_3^1 \land \beta^1_{3j}= \beta^2_{3j})\]\\
-Third, considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up to renaming)  we have: 
+Therefore, we have for all $j\in J'_{13}$ (recall that $J'_{13}=J'_{23}$):  \[\beta_{13j} = \beta_{23xj} \Rightarrow (j\in J_1 \land \beta_{1j} = \beta_{2xj}) \vee (j\in J_3^1 \land \beta^1_{3j}= \beta^2_{3j})\]
+(iii) Considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up to renaming)  we have: 
 ${\displaystyle V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}} \vdash \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$
@@
 
-From all the implications induced by the extension of the valuation context mentioned above, and by entering   all previous intermediate results in the formula $(*)$, we get:
+From all the implications induced by the extension of the valuation context mentioned above in the formula $(*)$ and by using the results (i), (ii) and (iii), we get:
 \begin{multline*}
@@
 
-We can deduce for any transition $t_3$ in $A_3$ relying $s_3$ and $s^{\prime}_3$ we have:
+Moreover, we have  for any transition $t_3$ in $A_3$ relying $s_3$ and $s^{\prime}_3$ the following:
 \begin{multline*}
@@
  \end{multline*}	
-Therefore, we get:
+From the two previous formulas, we get:
 \begin{multline*}
@@
 			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\land\\
-			 \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+			  R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge
  \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3) \wedge s^{1\prime}_3 = s^{2\prime}_3
@@
 \end{multline*}
-And finally by hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
+And finally by hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,   by definition of reachability (Definition \ref{Def:Reach}) we obtain $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
 \[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
@@
 \begin{multline*}
-V_{13} \uplus V_{23} \uplus \fvars{t_1}  \cap \fvars{t_{13}} \vdash\\
+V_{13} \uplus V_{23} \uplus  \fvars{t_{13}} \vdash\\
 R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \reach{A_{13}}\mpar{s_{13}}
@@
 \end{multline*}	
-Because of the independence of the substitution domains, we get the expected formula:
+Because of the independence of the substitution domains, we simplify and get the expected formula:
 	\begin{multline*}
@@
 \item if $k \notin J'_1$:\\
-The proof of this case follows the same steps as the previous case the only argument that changes is that  $g_{13} \Leftrightarrow g_1$ and
+The proof of this case follows the same steps as the previous case the only argument that changes is that by composition we obtain:  $g_{13} \Leftrightarrow g_1$ and
 $g_{23x}  \Leftrightarrow g_{2x}$.
@@
 \end{multline*}
-We have a second hypothesis stating that the result of the composition \(A_1\subst{A_3}{k}\) is non-blocking, which leads to:
+We extend the valuation to cover the variables of  $t^2_3$ in $t_{23}$ and using their value in $t_3$ and because the following statement holds: $\fvars{t_{13}} \vdash \reach{A_{13}}\mpar{s_{13}}$, we get:
+\begin{multline*}
+V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}  \wedge \reach{A_{13}}\mpar{s_{13}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}   \wedge \reach{A_{13}}\mpar{s_{13}}\right)
+\end{multline*}
+We have a second hypothesis stating that the result of the composition \(A_1\subst{A_3}{k}\) is non-blocking, by Definition \ref{Def:Non-blockcomp} we have:
 \begin{multline*}
@@
 \end{multline*}
-We use the the first, we extend the valuation to cover the variables of  $t^2_3$ in $t_{23}$ using their value in $t_3$ and because $\fvars{t_{13}} \vdash \reach{A_{13}}\mpar{s_{13}}$, we get:
-\begin{multline*}
-V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}  \wedge \reach{A_{13}}\mpar{s_{13}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}   \wedge \reach{A_{13}}\mpar{s_{13}}\right)
-\end{multline*}
-By transitivity with the second hypothesis we obtain:
+By transitivity  we obtain:
 \begin{multline*}
@@
 \end{multline*}
-That implies:
+
+Considering that each valuations $\sigma_{3}^1$ and $\sigma_{3}^2$ associate the same values to the ``same'' variables modulo renaming, so the following holds:\\ $\left(\,\,{\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{3}^1 \uplus \sigma_{3}^2 }$, we obtain:
 \begin{multline*}
@@
 $A_1\subst{A_3}{k}$),  to prove the theorem it is sufficient to prove that there exists a relation between states of the two open automata that satisfies the conditions of the Definition \ref{Def:OA-Refinement}.
-
 We denote $A_1=  \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}$ and \(A_2 = \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and $A_3 = \OA{S_3}{s_{03}}{J_3}{V_3}{\sigma_{03}}{T_3}$.
@@
  v^1_1=v^2_1\wedge s^1_1 = s^2_1\]
-Let us denote $H'=H\cup J_1 \setminus\{k\}$.
-We want to prove that $\mpar{R', H'}$  is a hole-tracking simulation of $A_{12}$ and $A_{13}$. As for the previous proof we deal with cases:
+Let us denote $H'=H\uplus J_1 \setminus\{k\}$.
+We want to prove that $\mpar{R', H'}$  is a hole-tracking simulation of $A_{12}$ and $A_{13}$. As for the previous proof we proceed by cases:
 \begin{enumerate}
@@
 \[\sigma_{012} \uplus \sigma_{013} \vdash R'\mpar{s_{012}, s_{013}}\]
-with $\sigma_{012} = \sigma_{01}^1 \uplus \sigma_{02}$, $\sigma_{013} = \sigma_{01}^2 \uplus \sigma_{03}$, $s_{012}=(s_{01}^1,s_{02})$, and $s_{013}=(s_{01}^2,s_{03})$.\\
+with $\sigma_{012} = \sigma_{01}^1 \uplus \sigma_{02}$, $\sigma_{013} = \sigma_{01}^2 \uplus \sigma_{03}$, $s_{012}=(s_{01}^1,s_{02})$, and $s_{013}=(s_{01}^2,s_{03})$.
 By using the fact that $R$ relates initial configurations of  $A_2$ and $A_3$, we have  the following statement:
-$\mpar{\sigma_{02} \uplus \sigma_{03} \vdash R\mpar{s_{02}, s_{03}}}$,  and relying on the  fact that initial states are reachable $\sigma_{012} \vdash \reach{A_{12}}\mpar{s_{012}}$ we have:
+$\mpar{\sigma_{02} \uplus \sigma_{03} \vdash R\mpar{s_{02}, s_{03}}}$,  and based on the  fact that initial states are reachable $\sigma_{012} \vdash \reach{A_{12}}\mpar{s_{012}}$ we have:
 \[ \mpar{\sigma_{02} \uplus \sigma_{03} \vdash R\mpar{s_{02}, s_{03}}} \wedge 
@@
 \end{align*}		
-there exists an indexed family $t_{13x}$ of OTs originating from $s_{13}$ that simulates it: 
+there exists an indexed family $t_{13x}$ of OTs originating from $s_{13}$ that simulate it: 
 \begin{align*}
@@
 Consider any transition $t_{12}$ in $A_{12}$,  $t_{12}$ is obtained (by case analysis on the definition of composition) 
-
-* either by the composition of a transition $t_2=\OTx{2}{}{2}{2}$ and a transition \[t_1^1=
+\begin{enumerate}
+\item either by the composition of a transition $t_2=\OTx{2}{}{2}{2}$ and a transition \[t_1^1=
 \OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{   {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1} \qquad \text{ when } k \in {J^1_{1}}^{\prime}
@@
 
-* or by an the transition $t_1^1=
+\item  or by  the transition $t_1^1=
 \OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{{(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1}$  alone with the state $s_2$ unchanged, if $k \not\in {J^1_{1}}^{\prime}$
@@
 \[t_{13x} = \left(\OT{\mpar{s^2_1, s_3}}{\mpar{{s^2_1}', s_{3}}}{\alpha_1^2}{ {(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{g^2_1}{\psi^2_1} \right)^{x\in X}\]
-
-According to how the transition $t_{12}$ is built we have to consider both cases to prove the following:
- $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$ and
+\end{enumerate}
+We have to  prove the following formula in both cases (depending on how the transition $t_{12}$ is built): $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$ and
 \begin{multline*}	
@@
 As before, the proof  is based  on the fact that the composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.
-By construction of  $t_{12}$ and $t_{13}$ we have $\alpha_{12}=
+(i)  By construction of  $t_{12}$ and $t_{13}$ we have $\alpha_{12}=
 \alpha^1_{1}$ and $\alpha_{13x}=\alpha^2_{1}$. As  $\alpha^1_{1}=\alpha^2_{1}$  we deduce: 
-$\alpha_{12} = \alpha_{13x}$. In addition we have:\\
+$\alpha_{12} = \alpha_{13x}$. (ii) In addition we have:\\
  $\beta_{12j}^{j\in J'_{12}}= {({\beta^1_{1j}})^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {\beta_{2j}^{j \in J^{\prime}_2} }}$ and $\beta_{13xj}^{j\in J'_{13}}= {{(\beta^2_{1j})^{j \in {J^{2 \prime}_1} \setminus \{k\}}}\uplus \beta_{3xj}^{j \in J'_{3x} } }$
@@
 \[\beta_{12j} = \beta_{13xj} \Rightarrow (j\in J^{1 \prime}_1 \land \beta^1_{1j}= \beta^2_{1j}) \vee  (j\in J'_2 \land \beta_{2j} = \beta_{3xj})  \]
-Third, considering $\beta^1_{1j}$ and  $\beta^2_{1j}$  are the same (up to renaming)  we have: 
+(iii) Considering $\beta^1_{1j}$ and  $\beta^2_{1j}$  are the same (up to renaming)  we have: 
 ${\displaystyle V^1_{1} \uplus V^2_{1} \uplus \fvars{t_{1}} \vdash \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1\implies \bigwedge_\subbox{j \in J^{\prime}_1} \beta^1_{1j}= \beta^2_{1j}}$.
@@
 
-By entering all the intermediate results  into the formula $(*)$ we get:
+From the results (i), (ii), (iii)  and the formula $(*)$ we get:
 \begin{multline*}
@@
 \end{multline*}	
-which can be simplified and rewritten as follows:
+which can be simplified and re-written as follows:
 \begin{multline*}
@@
 \end{multline*}	
-For any transition $t_1$ in $A_1$ relying $s_1$ and $s^{\prime}_1$ and for each $x \in X$ we have:
+Furthermore, we have for any transition $t_1$ in $A_1$ relying $s_1$ and $s^{\prime}_1$ and for each $x \in X$ :
 \begin{multline*}
@@
 
-From the hypothesis, we have \(A_1\subst{A_2}{k}\) is non-blocking.  Then   Definition \ref{Def:Reach} we have  for all $t_{12} \in T_{12}$:
+From the hypothesis, we have \(A_1\subst{A_2}{k}\) is non-blocking.  Then, by definition of the reachability  (Definition \ref{Def:Reach}) we have  for all $t_{12} \in T_{12}$:
 \[ \fvars{t_{12}} \vdash \left(\reach{A_{12}}\mpar{s_{12}} \wedge g_{12} \implies \reach{A_{12}}\mpar{s_{12}'}\psubst{\psi_{12}}\right) \]	
-With the conjunction of the  formula obtained above and after simplifying, we get:
+With the conjunction of the  formula obtained above and after simplifying, we get the expected result:
 \begin{multline*}	
@@
 	\end{multline*}
-\item It remains to prove the  satisfaction of the  deadlock reducing condition. According to the relation between   $A_2$ and $A_3$ we have for all $\mpar{s_{2p}, s_3} \in S_2 \times S_3$:
-\begin{multline*}
- V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash \left(R_{23}\mpar{s_{2p}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} \right)
-\end{multline*}
-By adding the term $R_{12}\mpar{s_1,s_{2p}}$ to both sides of the implication, we get:
-
+\item if $k \notin J^{1\prime}_1$:\\
+The proof of this case follows the same steps as the previous case the only argument that changes is that by composition we obtain:  $g_{12} \Leftrightarrow g^1_1$ and
+$g_{13x}  \Leftrightarrow g^1_{2}$.
 	\end{itemize}
+
+\item It remains to prove the  satisfaction of the  deadlock reducing condition:  for all $\mpar{s_{12}, s_{13}} \in S_{12} \times S_{13}$
+\begin{multline*}
+V_{12} \uplus V_{13} \uplus \biguplus_\subbox{t_{13}\in \fOT{s_{13}}} \fvars{t_{13}} \vdash \\ \left(R^{\prime}\mpar{s_{12}, s_{13}} \wedge \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \implies \bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}} \right)
+\end{multline*}
+
+Let's start with the hypothesis  stating that $\wrel{A_2}{A_3}{H}$, thus we have for all $\mpar{s_{2}, s_3} \in S_2 \times S_3$:
+\begin{multline*}
+ V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash \left(R\mpar{s_{2}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_{2p} \in \fOT{s_{2}}} \fguard{t_{2}} \right)
+\end{multline*}
+By adding the same term ${\displaystyle \reach{A_{12}}\mpar{s_{12}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}$ to both sides of the implication, we get:
+\begin{multline*}
+ V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash\\ R\mpar{s_{2}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \wedge \reach{A_{12}}\mpar{s_{12}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies\\ \bigvee_\subbox{t_{2p} \in \fOT{s_{2}}} \fguard{t_{2}} \wedge \reach{A_{12}}\mpar{s_{12}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
+\end{multline*}
+that can be re-written
+\begin{multline*}
+ V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash\\ R\mpar{s_{2}, s_3} \wedge \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \wedge \reach{A_{12}}\mpar{s_{12}}  \implies \bigvee_\subbox{t_{2} \in \fOT{s_{2}}} \fguard{t_{2}} \wedge \reach{A_{12}}\mpar{s_{12}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
+\end{multline*}
+
+Yet we have by hypothesis  \(A_1\subst{A_2}{k}\) is non-blocking, by definition of non-blocking composition (Definition \ref{Def:Non-blockcomp}) we have:
+\begin{multline*}
+ V_{12} \uplus  \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash
+ \reach{A_{12}} \mpar{s_{12}}  \wedge  \bigvee_\subbox{t_{1} \in \fOT{s_{1}}} \fguard{t_{1}}  \implies \bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}
+\end{multline*}
+From the two previous formulas and considering that each valuations $\sigma_{1}^1$ and $\sigma_{1}^2$ associate the same values to the ``same'' variables modulo renaming we obtain the expected result.
 

### 2022-03-24 2016-Weak-FH-Bisim/WeakBisim.tex
format jlamp + positioning again

--- 2021-10-22 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
-\documentclass{lmcs}
+\documentclass{elsarticle}
 %\overfullrule=1mm
@@
 \usepackage{proof}
-%\usepackage{setspace}
+\usepackage{makecell}
 %\usepackage{indentfirst}
-\usepackage{amsmath,amssymb,amscd,mathrsfs}
 \DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
@@
 \usepackage{macrospNets}
-
+\usepackage{amsmath,amssymb,amscd,mathrsfs}
 \newcommand{\nounderline}[1]{#1}
@@
 
-\newtheorem{theorem}{Theorem}
+\newtheorem{thm}{Theorem}
 %\newtheorem{prop}{Proposition}
 %\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{lemma}{Lemma}
-\newtheorem{algorithm}[theorem]{Algorithm}
+\newtheorem{lem}{Lemma}
+\newtheorem{algorithm}[thm]{Algorithm}
 %\newtheorem{remark}[theorem]{Remark}
-\newtheorem{definition}{Definition}
+\newdefinition{definition}{Definition}
 \newtheorem{property}{Property}
-\newtheorem{example}{Example}
+\newdefinition{example}{Example}
 %\newtheorem{problem}[theorem]{Problem}
-%\newenvironment{proof}{\paragraph{Proof}}{}
+\newproof{proof}{Proof}
 
@@
 }         
-\email{rabea.ameur-boulifa@telecom-paris.fr}
+\ead{rabea.ameur-boulifa@telecom-paris.fr}
 
@@
 \address{Univ Lyon, EnsL, UCBL, CNRS, Inria,  LIP, F-69342, LYON Cedex 07, France.}
-\email{ludovic.henrio@cnrs.fr}
+\ead{ludovic.henrio@cnrs.fr}
 
@@
 \address{INRIA Sophia Antipolis M\'edit\'erann\'ee, UCA, BP 93, 06902 Sophia Antipolis, France}
-\email{eric.madelaine@inria.fr}
+\ead{eric.madelaine@inria.fr}
 %\date{}                                           % Activate to display a given date or no date
@@
 
-\subsubsection*{pNets and open automata}
+\subsubsection*{pNets}
 pNet is a convenient model to model concurrent systems in a hierarchical and parameterised way.
@@
 Open pNets are pNets for which some elements in the hierarchy are still undefined, such undefined elements are called \emph{holes}; a hole can be \emph{filled} later by providing another pNet.
+This article first defines pNets and illustrates with an example how they can be used to provide the model of a communicating system.
+
+\subsubsection{A semantics for Open pNets based on open automata}
 The semantics of pNets can be expressed as a translation to a labelled transition system, but only if the pNet has no parameter and no hole.
 Adding parameters to a LTS is quite standard but enabling holes inside LTSs is not a well-defined notion.
-We thus define \emph{open automata} that can be seen as LTSs with parameters and holes.
+
+To define a semantics for open pNets we thus need LTSs that can have two kinds of parameters: \emph{variable} and \emph{processes}.
+We call such LTSs with parameters and holes and equiped with a composition operation, \emph{open automata}.
+The main goal of this article is to define the theory behind open automata and to use them to provide a semantics and prove composition properties for open pNets.
   The transitions of open automata are much more complex than transitions of an LTS as the firing on a transition depends on parameters and actions that are symbolic.
@@
 
-Contrarily to pNets, open automata are not hierarchical structures, thus they are more convenient for formal reasoning but not adapted to the definition of a complex and structured system like pNets.
-Additionally, open transitions are expressed in terms of logics more than in terms of synchronised actions, synchronisation vectors on the contrary make it easy to express synchronisations that exist in process algebra or in specification and high-level languages for distributed systems.
-
-This article defines pNets and illustrates with an example how they can be used to provide the model of a communicating system.
-Then we introduce open automata to provide a semantics to open pNets and introduce bisimulation relations and their properties.
-Open automata can be also seen as an algebra that can be studied independently from its application to pNets but their composition properties make more sense in a hierarchical model like pNets.
+Contrarily to pNets, open automata are not hierarchical structures, we consider them here as a mathematical structure convenient for formal reasoning but not adapted to the definition of a complex and structured system.
+Open transitions are expressed in terms of logics while the communication in pNets is specified as synchronisation vectors that specify synchronised actions.
+Open automata could alternatively be  seen as an algebra that can be studied independently from its application to pNets but their composition properties make more sense in a hierarchical model like pNets.
 
@@
 \[
-\begin{array}[l]{rcl@{\quad}p{7.5cm}}
+\begin{array}[l]{rcl@{\quad}p{5.65cm}}
   \alpha\in\AlgA&::=&a(p_1,\ldots,p_n)&\text{action terms}\\
-  p_i&::=& ?x~|~e_i&\text{parameters (input variable or expression)}\\
+  p_i&::=& ?x~|~e_i&\text{parameters (input var or expression)}\\
   e_i&::=& \symb{Value}~|~x~|~\symb{op}(\symb{e}_1,..,\symb{e}_n)&\text{Expressions}
@@
 %\ERIC{Une definition plus correcte serait peut-etre:}\\
-
-\[(x_{k}\gets e_{k})^{k\in K}\shortodot (x'_{k'}\gets e'_{k'})^{k'\in K'} =  
-(x_{k}\gets e_{k}\subst{(x'_{k'}\gets e'_{k'})^{k'\in K'}})^{k\in K} \cup (x'_{k'}\gets e'_{k'})^{k'\in K''}\]
-where $K''=\{k'\in K'|x'_{k'}\not\in\{x_k\}^{k\in K}\}$
+\begin{align*}
+(x_{k}\!\gets\! e_{k})^{k\in K}\odot (x'_{k'}\gets e'_{k'})^{k'\in K'} \!=&  
+(x_{k}\gets e_{k}\subst{(x'_{k'}\!\gets\! e'_{k'})^{k'\in K'}})^{k\in K} \\&\cup (x'_{k'}\!\gets\! e'_{k'})^{k'\in K''}
+\end{align*}where $K''=\{k'\in K'|x'_{k'}\not\in\{x_k\}^{k\in K}\}$
 %
@@
 \begin{definition}[pNet composition]
-	An open pNet: $\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
+	An open pNet: $\pNet \!=\! \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
 	\set{\symb{SV}}\,\myrangle$
@@
 
+\fussy
 Figure \ref{SimpleProt:Impl} shows the pNet model of the protocol implementation, called $\symb{SimpleProtocolImpl}$.
@@
 The $\symb{Sender}$ increments its local error counter $ec$, and resends the message (including $ec$) to the $\symb{Medium}$, that will, eventually, transmit $m,ec$ to the $\symb{Receiver}$.
+\sloppy
 %Strictly speaking, as variables are local to each  state, we have two distinct $ec$ variables in the \textit{Sender} pLTS, one in state \texttt{s1}, another one in state \texttt{s2}, the value of the variable is updated along the transitions entering each of the two states.
@@
 	I_2$}\footnote{We could replace $I_1$ and $I_2$ by their formal definition in \textbf{Tr2} but the rule would be more difficult to read.}.   
+\end{itemize}                                                                  
 \begin{mathpar}
@@
     	K}\myrangle) \!=\! \pLTS_l^{\,l\in L} \quad  	
-k\!\in\! K \quad SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
+k\!\in\! K \\\\ SV_k \!=\! \SV{(\alpha'_m)^{m \in I_1\uplus I_2\uplus J}}{\alpha'}{e_b} 
 \\
@@
     		\ostate{(s_i^\prime)^{i\in L_m}}} }	
-  \qquad
+  \\\\
 \forall m\!\!\in\!\! I_2.		{ \pNet_m 
@@
     	{\ostate{s_m} \OTarrow {\alpha_m}
-    		\ostate{s_m'}} }\\\\
+    		\ostate{s_m'}} }\qquad
     J' = \biguplus_{m\in I_1}\!\! J_m \uplus J	\\
-    	\Pred = \bigwedge_{m\in I_1\uplus I_2}\!\! \Pred_m \land
+    	\Pred = \!\!\bigwedge_{m\in I_1\uplus I_2}\!\! \Pred_m \land
     	\Predsv(SV_k,\alpha_m^{m\in I_1\uplus I_2},\beta_j^{j\in J},\alpha)\\ 
@@
 \end{mathpar}
-\end{itemize} 
+
 	\medskip
@@
 \begin{figure}[ht]
-   \centerline{\includegraphics[width=13cm]{XFIG/SPSpecOpen}}
+   \centerline{\includegraphics[width=\linewidth]{XFIG/SPSpecOpen}}
    \caption{Open automaton for  $\symb{SimpleProtocolSpec}$}
@@
  \begin{figure}[ht]
-  \centerline{\includegraphics[width=15cm]{XFIG/SPImplOpen}}
+  \centerline{\includegraphics[width=\linewidth]{XFIG/SPImplOpen}}
   \caption{Open automaton for $\symb{SimpleProtocolImpl}$}  \label{SimpleProtCounter:ImplOA}
@@
 				 } {s \OTWeakarrow {\alpha} s'} \in \WT
-}\qquad \WTDeux
+} \WTDeux
 %\inferrule{
@@
          {s_1 \OTWeakarrow {\alpha} s_2} \in \WT
-\qquad
+\\\\
 \openrule
@@
 \begin{figure}[ht]
-   \centerline{\includegraphics[width=13cm]{XFIG/WOT2-result}}
+   \centerline{\includegraphics[width=\linewidth]{XFIG/WOT2-result}}
   \caption{Construction of an example of weak open transition}
@@
 \begin{figure}[h]
-   \centerline{\includegraphics[width=15cm]{XFIG/SPSpecWeakOpen}}
+   \centerline{\includegraphics[width=\linewidth]{XFIG/SPSpecWeakOpen}}
   \caption{Weak Open Automaton of  $\symb{SimpleProtocolSpec}$}
@@
 
-$ \forall n\ge 0.\, WI_3(n) = \openrule
-  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, True,
+$ \forall n\ge 0.\, \symb{WI}_3(n) = \openrule
+  {\{\texttt{P}\mapsto \texttt{p-send(m)}\}, \symb{True},
     (\texttt{s\_msg}\gets \texttt{m}, \texttt{s\_ec}\gets n)}
@@
 
-$  \forall n\ge 0.\, WI_4(n) = \openrule
-         {\{\}, True, 
-   (\texttt{m\_msg}\!\gets\! \texttt{s\_msg}, \texttt{m\_ec}\!\gets\! \texttt{s\_ec}+n, \texttt{s\_ec}\!\gets\! \texttt{s\_ec}+n)}
+$\hspace{-6pt}  \forall n\!\ge\! 0.\, \symb{WI}_4(n) \!=\! \openrule
+         {\{\}, \symb{True}, 
+   (\texttt{m\_msg}\!\gets\! \texttt{s\_msg}, \texttt{m\_ec}\!\gets\! \texttt{s\_ec}\!+\!n, \texttt{s\_ec}\!\gets\! \texttt{s\_ec}\!+\!n)}
          {100 \OTWeakarrow {\tau} 210}
@@
 
-$  \forall n\ge 0.\, WI_{456}(n) = \openrule
-         {\{\}, True, 
+$  \forall n\ge 0.\, \symb{WI}_{456}(n) = \openrule
+         {\{\}, \symb{True}, 
     (\texttt{s\_ec}\gets \texttt{s\_ec}+n)}
@@
 \begin{array}{l@{}l}
-Post_{6a}&= post_{4}\shortodot\ post_{456*}\shortodot\ post_{6}\\ 
-&=  (\texttt{m\_msg}\gets \texttt{s\_msg}, \texttt{m\_ec}\gets \texttt{s\_ec})\,
-\shortodot (\texttt{s\_ec}\gets \texttt{s\_ec}+n) 
-\shortodot (\texttt{s\_ec}\gets \texttt{s\_ec}+1) \\
-&= (\texttt{m\_msg}\!\gets \texttt{s\_msg}, \texttt{m\_ec}\!\gets \texttt{s\_ec}+1\!+\!n, \texttt{s\_ec}\!\gets \texttt{s\_ec}+1\!+\!n)
+\symb{Post}_{6a}&= post_{4}\shortodot\ post_{456*}\shortodot\ post_{6}\\ 
+&= \! (\texttt{m\_msg}\!\gets\! \texttt{s\_msg}, \texttt{m\_ec}\!\gets\! \texttt{s\_ec})\,
+\!\shortodot (\texttt{s\_ec}\!\gets\! \texttt{s\_ec}\!+\!n) 
+\shortodot (\texttt{s\_ec}\!\gets\! \texttt{s\_ec}\!+\!1) \\
+&= \!(\texttt{m\_msg}\!\gets \texttt{s\_msg}, \texttt{m\_ec}\!\gets \texttt{s\_ec}+1\!+\!n, \texttt{s\_ec}\!\gets \texttt{s\_ec}+1\!+\!n)
 \end{array}
@@
  and  
-\begin{multline*}
-\Pred_{s,t} \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
+\begin{align*}
+&\Pred_{s,t}\land \Pred_{OT} \implies\\
+&  \displaystyle{\bigvee_{x\in X}\!
    \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
@@
      \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)}
-\end{multline*}
+\end{align*}
 
@@
 In the case of weak FH-Bisimulation, the proof obligation from Definition \ref{def-Weak-bisim} becomes:
-      \begin{multline*}
-\forall fv_{OT}.\, \Big\{ \Pred_{s,t} \land \Pred_{OT} \implies\\
- \bigvee_{x\in X}\!
+\begin{small}
+      \begin{align*}
+&\forall fv_{OT}.\, \Big\{ \Pred_{s,t} \land \Pred_{OT} \implies\\
+& \bigvee_{x\in X}\!
   \left[\exists fv_{OT_x}.
-    \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
+    \left( \forall j\!\in\! J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
      \!\land\! \alpha\!=\!\alpha_x\! \land\!  
-     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)\right]\Big\}
-\end{multline*}
+     \Pred_{s',t_x}\subst{\Post_{OT}\!\uplus\!\Post_{OT_x}}\right)\right]\!\Big\}
+\end{align*}
+\end{small}
 
@@
 \begin{tabular}{cp{.53\linewidth}}
- \begin{minipage}{.43\linewidth}
- \includegraphics[width=\linewidth]{XFIG/Choice.pdf}\vspace{-18ex}
+ \begin{minipage}{.4\linewidth}
+ \includegraphics[width=1.04\linewidth]{XFIG/Choice.pdf}\vspace{-18ex}
 \end{minipage} 
@@
     \item Both pNets trivially verify the ``non-observability''
-      condition: the only vectors having $\tau$ as an action of a
+      condition: the  vectors having $\tau$ as an action of a
       sub-net are of the form ``$< -, \tau, -> \rightarrow \tau$''.
@@
 \hline
-     \symb{SimpleProtocolSpec} states&   \symb{SimpleProtocolImpl} states& Predicate\\
+     \makecell{\symb{SimpleProtocolSpec}\\ states}&   \makecell{\symb{SimpleProtocolImpl}\\ states}& Predicate\\
     \hline
@@
 %       
-%              \begin{proof}
-       	\proof
+              \begin{proof}
+%       	\proof
        	It is trivial to check reflexivity and symmetry. Here we focus on the
@@
        	proof is similar.
-
-%       \end{proof}
 \qed
+
+       \end{proof}
 
@@
 
-%   \begin{proof}
-\proof
+   \begin{proof}
 Consider rule \TrDeux\ in 
@@
  \end{small}
-%\end{proof}
-  \qedhere
+\qed
+\end{proof}
 
@@
 
-\proof
-%\begin{proof} 
+\begin{proof} 
 Let $P=\mylangle {\pNet}_m^{m\in I}, \set{\Sort}, \symb{SV}_k^{k\in K}\myrangle$.
@@
 \end{small}
-   This provides the desired conclusion.   
-%  \end{proof}
-\qed
+   This provides the desired conclusion.   \qed
+
+  \end{proof}
 
@@
 \medskip
-%\begin{proof}
-\proof
+\begin{proof}
  The proof of Theorem~\ref{thm-congr-eq} exhibits classically a bisimulation relation for 
@@
 This proves the  condition of the FH-simulation, the other direction is 
- similar.
-%\end{proof}
-\qed
+ similar. \qed
+
+\end{proof}
         \subsection{Proof of Theorem ~\ref{thm-ctxt-eq}: Context equivalence}
@@
 \medskip
-\proof
-%\begin{proof}
+
+\begin{proof}
 The proof of Theorem~\ref{thm-ctxt-eq} exhibits  a bisimulation relation for a 
@@
 This proves the  condition of the FH-simulation, the other direction is 
-similar.
-%\end{proof}
-\qed
+similar. \qed
+\end{proof}
 
@@
 \end{lem}
-\proof %\begin{proof}
+\begin{proof}
  ($\Rightarrow$) We present an induction on $n$ and $m$, focusing on the incrementation on $n$: we prove that the property is valid for $m=-1$, $n=-1$ apply a first induction proof for going from $n$ to $n+1$, a similar induction can be applied to go from $m$ to $m+1$ (omitted).
@@
 
-This concludes the inductive step, showing  that the decomposition expressed by the $\Leftarrow$ direction of the lemma is always possible with the right side conditions. 
-\qedhere
+This concludes the inductive step, showing  that the decomposition expressed by the $\Leftarrow$ direction of the lemma is always possible with the right side conditions. \qed
 \end{itemize}
-%\end{proof}
+\end{proof}
 
@@
 
-%\begin{proof}
-\proof Note that Definition \ref{def-Weak-bisim} is a particular case of the definition above, thus we only need to prove one direction of the equivalence between the two definitions, namely: \\
+\begin{proof}
+ Note that Definition \ref{def-Weak-bisim} is a particular case of the definition above, thus we only need to prove one direction of the equivalence between the two definitions, namely: \\
 ($\Rightarrow$) We prove that Definition \ref{def-Weak-bisim} implies the definition above. In other words,
@@
    \underbrace{\Pred_{OT_a}\land\Pred_{OT_{b}} \subst{\Post_{OT_a}} \land 
-  \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortodot\Post_{OT_a}}}_{\Pred} \land  \underbrace{\alpha'\subst{\Post_1}}_{\alpha}=\underbrace{\alpha_{2 b} \subst{\Post_{OT_a}}}_{\alpha''} \\\land \Pred_{s_{31},c}  \subst{\underbrace{\Post_3\shortodot\Post_2\shortodot\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{c}}\shortodot \Post_{OT_{b}}\shortodot\Post_{OT_a}}_{\Post}}\Big)
+  \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortodot\Post_{OT_a}}}_{\Pred} \land\\  \underbrace{\alpha'\subst{\Post_1}}_{\alpha}=\underbrace{\alpha_{2 b} \subst{\Post_{OT_a}}}_{\alpha''} \\\land \Pred_{s_{31},c}  \subst{\underbrace{\Post_3\shortodot\Post_2\shortodot\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{c}}\shortodot \Post_{OT_{b}}\shortodot\Post_{OT_a}}_{\Post}}\Big)
 \end{multline*}
@@
 \Big(\forall j\in J.\gamma_j'=\gamma_j \land  \Pred \land \alpha=\alpha''  \land \Pred_{s',x}\subst{\Post_{OT}\uplus\Post\,}\Big)$
-%\end{proof}
-\qedhere
+\end{proof}
 
@@
 
-%\begin{proof} 
-\proof Suppose that we have: 
+\begin{proof} 
+ Suppose that we have: 
 \begin{mathpar}
@@
 \alpha=&\alpha'{\subst{\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}}\\
-\gamma_j^{j\in J}=&\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{0}\!\! \Post_{1j}}}\dotcup\  \vis{\set{\beta_2}\subst{\bigodot_{j=m_1}^{0}\Post_{1j}}} \dotcup  
+\gamma_j^{j\in J}=&\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{0}\!\! \Post_{1j}}}\dotcup\\&  \vis{\set{\beta_2}\subst{\bigodot_{j=m_1}^{0}\Post_{1j}}} \dotcup  
 {\mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}} }}
 \\
-\Pred=&\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}\land
+\Pred=&\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}\land\\&
 \bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}\\
@@
 		}%\]
-	\text{~~and~~} 
+	\text{~~and~~} \\
 		Q\models{\openrule
@@
 		}%\]
-	\,\text{~~and~~}
+	\,\text{~~and~~}\\
 	Q\models{\openrule
@@
 $\alpha''=\alpha'\displaystyle{\subst{\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}}}$\\
-On the other hand, we have:
+On the other hand, we have:\\
 $\alpha=\alpha'\displaystyle{\subst{\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}}}\displaystyle{\subst{\bigodot_{j=m_1}^{0}\!\!\Post\,''_{1j}}}=\alpha''\displaystyle{\subst{\bigodot_{j=m_1}^{0}\!\!\Post\,''_{1j}}}$.\\
 As $\displaystyle{\subst{\bigodot_{j=m_1}^{0}\!\!\Post\,''_{1j}}}$ has no effect on variables of $P$ and thus on variables of $\alpha''$, so we have $\alpha=\alpha''$.
-\\
+
 {\small \begin{align*}
@@
 \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\!\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}} }
-\\
+\end{align*}}
+{\small \begin{align*}
 \Pred\,'=&\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}}\land\\ 
@@
 				}%\]
-,~~$  
+,~~$  \\
 $ Q\models{\openrule
@@
 				}%\]
-,\quad
+,\\
 Q\models{\openrule
@@
 Consequently,  we have:
-\[\alpha'_{n_k}{\subst{\!\bigodot_{j=n_k-1}^{0}\!\!\!\Post\,''_{j}}} =
-\alpha'_{n_k}\displaystyle{\subst{\!\bigodot_{j=n_k-1}^{n'_{k}}\!\!\!\Post''_{j}\otimes\!\!\!\bigodot_{j=n'_{k}-1}^{0}\!\!\!\Post\,''_{j}}} = \alpha_k\displaystyle{\subst{\!\bigodot_{j=n'_{k}-1}^{0}\!\!\!\Post\,''_{j}}} =
+\[\alpha'_{n_k}{\subst{\!\bigodot_{j=n_k-1}^{0}\!\!\!\!\Post\,''_{j}}} \!=\!
+\alpha'_{n_k}\displaystyle{\subst{\!\!\bigodot_{j=n_k-1}^{n'_{k}}\!\!\!\!\Post''_{j}\odot\!\!\!\!\bigodot_{j=n'_{k}-1}^{0}\!\!\!\!\Post\,''_{j}}} \!=\!
+\alpha_k\displaystyle{\subst{\!\!\bigodot_{j=n'_{k}-1}^{0}\!\!\!\Post\,''_{j}}} \!=\!
 \alpha_k\displaystyle{\subst{\!\bigodot_{j=k-1}^{0}\!\!\Post_{j}}}\]
@@
 \begin{eqnarray*}
-\Pred_\beta &\iff& \gamma_{j_0}=
+\Pred_\beta &\iff& \gamma_{j_0}\!=\!
 \mybigdotcup_{p=0}^{p=n_1+n_2+2}
@@
 \gamma_j^{j\in J\cap \Holes(Q)}&=\mybigdotcup_{i=0}^{m_1} \vis{\set{(\beta_{1i}')}\subst{\bigodot_{j=i-1}^{0}\!\!
-\Post''_{1j}}}\dotcup  \vis{\set{\beta'_2}\subst{\bigodot_{j=m_1}^{0}\Post''_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{3i}} \subst{\bigodot_{j=i-1}^{0}\!\Post''_{3j}\shortodot\Post''_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post''_{1j}} }\\
+\Post''_{1j}}}\dotcup  \vis{\set{\beta'_2}\subst{\bigodot_{j=m_1}^{0}\Post''_{1j}}} \dotcup\\&\qquad\qquad \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{3i}} \subst{\bigodot_{j=i-1}^{0}\!\Post''_{3j}\shortodot\Post''_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post''_{1j}} }\\
 &=\mybigdotcup_{k=0}^n \left( \mybigdotcup_{i=n'_k}^{n'_{k+1}-1}\vis{\beta_{ij}^{j\in J\cap \Holes(Q)}\subst{\bigodot_{j=i-1}^{n'_k}\!\!\Post''_{j}\bigodot_{j=n'_k-1}^{0}\!\!\Post''_{j}}}\right)\\
@@
 %~~\qquad= \Post' \uplus \bigodot_{j=n}^{0} \Post_j $\\
-\qedhere
-%\end{proof}
+\qed
+\end{proof}
 
@@
 \end{lem}
-%\begin{proof}
-\proof
+\begin{proof}
 By  Lemma \ref{lem-rel-OT-WOT} we can decompose the WOT of $Q$ into  a series of $k+1$ and $k'+1$ tau open transitions and an $\alpha'_Q$ open transition (observable or not depending on $\alpha_Q$):
@@
 \begin{align*}
-\alpha_Q=&\alpha'_Q\displaystyle{\subst{\bigodot_{j=k}^{0}\Post_{1j}}}\\
-\set{\gamma}=&\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\!\!\bigodot_{j=h-1}^{0}\!\! \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigodot_{j=k}^{0}\!\!\Post_{1j}}} \dotcup%\\
+\alpha_Q=&\alpha'_Q\displaystyle{\subst{\bigodot_{j=k}^{0}\Post_{1j}}}
+\end{align*}
+\begin{align*}
+\set{\gamma}=&\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\!\!\bigodot_{j=h-1}^{0}\!\! \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigodot_{j=k}^{0}\!\!\Post_{1j}}} \dotcup\\&
 		%&
  \mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\!\!\bigodot_{j=h-1}^{0}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=k}^{0}\Post_{1j}} }\\
-\Pred_Q=&\bigwedge_{h=0}^{k}\!\Pred_{1h}\subst{\!\!\bigodot_{j=h-1}^{0}\!\!\!\!\Post_{1 j}}\land \Pred_2\subst{\bigodot_{h=k}^{0}\Post_{1h}}\land%\\
-%&
+\Pred_Q=&\bigwedge_{h=0}^{k}\!\Pred_{1h}\subst{\!\!\bigodot_{j=h-1}^{0}\!\!\!\!\Post_{1 j}}\land \Pred_2\subst{\bigodot_{h=k}^{0}\Post_{1h}}\land\\
+&
 	\!\bigwedge_{h=0}^{k'}\!\Pred_{3h}\subst{\!\! 	\bigodot_{j=h-1}^{0}\!\!\!{\Post_{3j}}\otimes{\Post_2}  \otimes\bigodot_{h=k}^{0}\!\!\Post_{1h}}\\
@@
 \end{align*}
-
 \end{small}
+
 \begin{enumerate}
@@
 &=\Pred_Q\land\Pred\land \alpha_Q=\beta_{j_0}\\[.3ex]
-\Post_c&=\Post\uplus\Post_Q \qedhere
+\Post_c&=\Post\uplus\Post_Q 
 \end{split}
 \end{equation*}
-%\end{proof}
-\qedhere
+\qed\end{proof}
+%\qedhere
 \smallskip
@@
     {{\beta_{1pj}^{j\in J_{1p}}},\Pred_{1p},\Post_{1p}   }
-         {\ostate{{(s_{1pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s_{1(p+1)i})}^{i\in L}}},  \quad
+         {\ostate{{(s_{1pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s_{1(p+1)i})}^{i\in L}}},  \\
 P\models\openrule
@@
 &\mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{3p}} \subst{\bigodot_{k=i-1}^{0}\Post_{3k}\shortodot\Post_2\shortodot\bigodot_{k=m_1}^{0}\Post_{1k}}}\\
-\Pred=&{\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\subst{\!\bigodot_{j=p-1}^{0}\!\!\Post_{1j}}\big)\land\Pred_2\subst{\!\bigodot_{p=m_1}^{0}\!\!\Post_{1p}}\land}%\\ 
-%&
+\Pred=&{\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\subst{\!\bigodot_{j=p-1}^{0}\!\!\Post_{1j}}\big)\land\Pred_2\subst{\!\bigodot_{p=m_1}^{0}\!\!\Post_{1p}}\land}\\ 
+&
 {\bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\bigodot_{j=p-1}^{0}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\bigodot_{p=m_1}^{0}\!\!\Post_{1p}}}\\
@@
 \vis{{\beta_{1ij_0}}\subst{\!\bigodot_{k=i-1}^{0} \!\!\!\!\Post_{1k} } }  \,\dotcup\, \vis{{\beta_{2j_0}}\subst{\!\bigodot_{k=m_1}^{0}\!\!\!\Post_{1k}}}}\dotcup\!
-%\\
-%&
+\\
+&\qquad\qquad
 { \!\mybigdotcup_{\substack{i=0\\j_0\in J_{3i}}}^{m_2}\!\! \vis{{\beta_{3ij_0}} \subst{\!\bigodot_{k=i-1}^{0}\!\!\!\Post_{3k}\shortodot\Post_2\shortodot
@@
  \mybigdotcup_{i=0}^{m_1}\set{\gamma'_{1i}}\subst{\bigodot_{k=i-1}^{0}\Post\,'_{1k}}\,\dotcup\,
-\set{\gamma'_{2}}\subst{\bigodot_{k=m_1}^{0}\Post\,'_{1k}}\,\dotcup
+\set{\gamma'_{2}}\subst{\bigodot_{k=m_1}^{0}\Post\,'_{1k}}\,\dotcup\\&\qquad
  \mybigdotcup_{i=0}^{m_2}\set{\gamma'_{3i}}\subst{\bigodot_{k=i-1}^{0}\Post\,'_{3k}\shortodot\Post\,'_2\shortodot\bigodot_{k=n}^{0}\Post\,'_{1k}}
@@
 \Pred\,''=&\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigodot_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigodot_{j=m_1}^{0}\Post\,'_{1j}}\land\\ 
-&\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigodot_{j=i-1}^{0}\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_2}^{0}\Post\,'_{1j}}\displaybreak[0]\\
+&\qquad\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigodot_{j=i-1}^{0}\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_2}^{0}\Post\,'_{1j}}\displaybreak[0]\\
 \Post\,''=&\bigodot_{j=m_2}^{0}\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{0}\Post\,'_{1j}
@@
 {\small \begin{equation*}
-\begin{split}\gamma'_j=&\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}}\subst{\bigodot_{k=i-1}^{0}\! \Post_{1k} } }  \dotcup  \vis{{\beta_{2j}}\subst{\bigodot_{k=m_1}^{0}\!\Post_{1k}}}\, \dotcup
+\begin{split}\gamma'_j=&\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}}\subst{\bigodot_{k=i-1}^{0}\! \Post_{1k} } }  \dotcup  \vis{{\beta_{2j}}\subst{\bigodot_{k=m_1}^{0}\!\Post_{1k}}}\, \dotcup\\&
 \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij} \subst{\!\bigodot_{k=i-1}^{0}\!\!\!\Post_{3k}\shortodot\Post_2\shortodot\bigodot_{k=m_1}^{0}\!\!\Post_{1k}}}
@@
 \mybigdotcup_{i=0}^{m_1}{\gamma'_{1ij}}\subst{\bigodot_{k=i-1}^{0}\Post\,'_{1k}}\dotcup
- {\gamma'_{2 j}}\subst{\bigodot_{k=m_1}^{0}\Post\,'_{1k}}\,\dotcup\, \mybigdotcup_{i=0}^{m_2}{\gamma'_{3ij}}\subst{\bigodot_{k=i-1}^{0}\Post\,'_{3k}\shortodot\Post\,'_2\shortodot\bigodot_{k=n}^{0}\Post\,'_{1k}}\\
+ {\gamma'_{2 j}}\subst{\bigodot_{k=m_1}^{0}\Post\,'_{1k}}\,\dotcup\\&\quad \mybigdotcup_{i=0}^{m_2}{\gamma'_{3ij}}\subst{\bigodot_{k=i-1}^{0}\Post\,'_{3k}\shortodot\Post\,'_2\shortodot\bigodot_{k=n}^{0}\Post\,'_{1k}}\\
 =&
@@
     \hline
-    $WI_1$ $WI_2$ $WI_\tau$ & $\{(s,s)| s \in \texttt{States of WOA}\} \cup \{(202,000)\} $ & 21 \\
+    $WI_1$ $WI_2$ $WI_\tau$ & $\{(s,s)| s \!\in\! \texttt{States of WOA}\} \!\cup\! \{(202,000)\} $ & 21 \\
     $WI_3(n)$ & \{(202,100),(000,100)\} & 2 \\
@@
 \hline
-    \symb{SimpleProtocolSpec} states & \symb{SimpleProtocolImpl} states & Predicate\\
+    \makecell{\symb{SimpleProtocolSpec}\\ states} & \makecell{\symb{SimpleProtocolImpl} \\states} & Predicate\\
     \hline
@@
   \item Triple ($\text{b0},  000,  True$) is in $\mathcal{R}$.
-  \item The verification condition \\
-    $\forall fv_{OT}. \{ \Pred \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!\!
-   \left[\exists fv_{OT_x}.
-  \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
-     \!\land\! \alpha\!=\!\alpha_x\! \land\!  
-     \Pred_{s',t_x}\subst{\Post_{OT}\!\uplus\!\Post_{OT_x}}\right)\right]\}}$
+  \item The verification condition 
+    \begin{align*}
+&\forall fv_{OT}. \{ \Pred \land \Pred_{OT} \implies\\
+&\quad \bigvee_{x\in X}\!\!
+   \big[\exists fv_{OT_x}.
+  \big( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
+     \!\land\! \alpha\!=\!\alpha_x\! \land \\
+&\qquad\qquad
+     \Pred_{s',t_x}\subst{\Post_{OT}\!\uplus\!\Post_{OT_x}}\big)\big]\}
+\end{align*}
 

### 2022-03-25 2016-Weak-FH-Bisim/WeakBisim.tex
JLAMP format

@@
 
-Establishing equivalences between programs or systems is crucial both for verifying correctness of programs, by establishing that two implementations are equivalent, and for justifying optimisations and program transformations, by establishing that a modified program is equivalent to the source one.
+Establishing equivalences between programs or systems is crucial both for verifying correctness of programs and for justifying optimisations and program transformations.
 There exist several equivalence relations for programs, and bisimulations are among the most versatile of these equivalences.
-Among bisimulation relations one distinguishes strong bisimulation, that requires that each action of a program is simulated by a single action of the equivalent program, a weak bisimulation that  is a coarser relation, allowing some of the actions to be
-  invisible or internal moves, and thus not simulated by the equivalent program.
+Among bisimulations one distinguishes strong bisimulation that requires that each action of a program is simulated by a single action of the equivalent program, and weak bisimulation that  allows some of the actions to be
+  invisible, and thus not simulated by the equivalent program.
 
@@
 placeholders inside the hierarchical structure  that can be filled later by sub-systems.
-%  Open pNets have a notion of \emph{synchronised actions}
-%  generalizing the usual internal actions (e.g. $\tau$ of CCS, or $i$
-%  in Lotos).
-
-This article defines bisimulation relations  for the comparison of systems specified as pNets.
+However, there is no standard tool for defining the semantics of an open system in this context, this article first defines \emph{open automata} that are labelled transition systems with parameters and holes.
+
+Relying on open automata, this article defines bisimulation relations  for the comparison of systems specified as pNets.
  We first define a strong bisimulation for open pNets.
-% \TODO{virer cette phrase, doublon du 1er paragraph? LUDO: OK} In practice, as happens in process algebras, strong bisimulation is too strong, and
-%  we define some coarser relations, taking into account
-%  invisible or internal moves.
   We then define an equivalence relation similar to
@@
 Among these properties we are interested in compositionality: if two systems are proven equivalent they will be undistinguishable by their context, and they will also be undistinguishable when their holes are filled with equivalent systems.
-We identify sufficient conditions on the automata to ensure compositionality of strong and weak bisimulation.
-The article is illustrated with a transport protocol running example; it shows the characteristics of our formalism and our bisimulation relations.
+We identify sufficient conditions to ensure compositionality of strong and weak bisimulation.
+The article is illustrated with a transport protocol running example.
 \end{abstract}
@@
 
-\subsubsection*{pNets}
+\paragraph{pNets}
 pNet is a convenient model to model concurrent systems in a hierarchical and parameterised way.
@@
 
-\subsubsection{A semantics for Open pNets based on open automata}
+\paragraph{A semantics for Open pNets based on open automata}
 The semantics of pNets can be expressed as a translation to a labelled transition system, but only if the pNet has no parameter and no hole.
@@
 
-To define a semantics for open pNets we thus need LTSs that can have two kinds of parameters: \emph{variable} and \emph{processes}.
+To define a semantics for open pNets we thus need LTSs that have both standard variable parameters, and process parameters, i.e.
+holes that can be filled by processes.
 We call such LTSs with parameters and holes and equiped with a composition operation, \emph{open automata}.
@@
 %In general $x_i,y_i$ range over variables.
-\subsubsection*{Term algebra.}
+\paragraph{Term algebra.}
 Our models rely on a notion of parameterised actions, that are
@@
 We define two kinds of parameterised actions. The first kind distinguishes input variables and the second kind does not. 
-We first define the set of actions that distinguish input variables, they will be used in the definition of \pLTS\ below:
+The  actions that distinguish input variables will be used in the definition of \pLTS\ below and are defined as follows:
 \[
@@
 
-\subsubsection*{Indexed sets}
-
-In this article, we extensively use indexed structures 
+\paragraph{Indexed sets}
+
+This article extensively uses indexed structures 
 (maps) over some countable indexed sets.   The indices can typically be
@@
 
-\subsubsection*{Substitutions}
+\paragraph{Substitutions}
 \label{def:substitutions}
@@
  $\subst{\Post}$ is  the operation that applies,  in a parallel manner,  the substitution defined by the partial function $\Post$.
-$\odot$ is a composition operator on these partial functions, such that for any term $t$ we have: $t\subst{\Post\shortodot\Post'} = (t\subst{\Post'})\subst{\Post}$.
+$\odot$ is a composition operator on these partial functions, such that for any term $t$ we have: $t\subst{\Post\odot\Post'} = (t\subst{\Post'})\subst{\Post}$.
 This property must also be valid when the substitution does not operate on all variables.
@@
 
-The semantics of the assignments is that a set of assignments between two states is performed in parallel so that their order do not matter and they all use the values of variables before the transition (or the values received as action parameters).
+A set of assignments between two states is performed in parallel so that their order do not matter and they all use the values of variables before the transition or the values received as action parameters.
 
@@
 \item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
-  synchronisation vectors. $\forall k\!\in\! K.\,
+  synchronisation vectors.\\ $\forall k\!\in\! K.\,
   \symb{SV}_k\!=\!\SV{\alpha_{l}^{l\in I_k \uplus J_k}}{\alpha'_k}{e_k}$ where
@@
 pNets have been used to model GCM distributed component systems, illustrating the expressiveness of the model~\cite{AmeurBoulifa2017}. 
-These works show that pNets are convenient to express the behaviour of the system in a compositional way, which is crucial for the definition of the semantics, especially when dealing with a hierarchical component system.
+These works show that pNets are convenient to express the behaviour of a system in a compositional way. 
 Unfortunately, the semantics of pNets and the existing tools at this point were only able to deal with a closed system completely instantiated: pNets could be used as composition operator in the definition of the semantics, which was sufficient to perform finite-state model checking on a closed system, but there was no theory for the use of pNets as operators and no tool for proving properties on open system.
 Consequently, much of the formalisation efforts did not use holes and the interplay between holes, sorts, and synchronisation vector was not formalised.
-In previous works~\cite{AmeurBoulifa2017}, only closed pNets were equipped with a semantics, it was defined as labelled transition systems which are instantiations of pNets. 
+In previous works~\cite{AmeurBoulifa2017}, only closed pNets were equipped with a semantics, it was defined as labelled transition systems. 
 %The old semantics is not necessary to understand this article but it defines the semantics of pNets in a simpler and more operational setting. 
@@
 % a bisimulation
-an equivalence between the semantics presented in this article and the operational one shown in~\cite{AmeurBoulifa2017} is outside the scope of this article.
+an equivalence between the semantics presented in this article and the operational one shown in~\cite{AmeurBoulifa2017} is outside the scope of this article because we focus here on the modelisation of holes that were not modelled in the previous semantics.
 
@@
 The assignments are applied simultaneously because the variables in $V$ can be in both sides ($x_k$s are distinct).
-
  Open transitions are identified
@@
 allows us to refine the predicate, or substitute any free variable by
-an expression as expressed below.
-
-For all predicate $\Pred$ for all partial function $\Post$,if $V\!\cap \!\dom(\Post)=\emptyset$, we have: 
+an expression. Formally, for all predicate $\Pred$ for all partial function $\Post$, if $V\!\cap \!\dom(\Post)=\emptyset$, we have: 
 		 \begin{mathpar}
@@
 For any open transition $OT$ in $\mathcal{T}_1$:\\
-\begin{minipage}{0.67\linewidth}  \begin{mathpar}
+\begin{minipage}{0.61\linewidth}  \begin{mathpar}
      \openrule
@@
 \hspace{2mm}
-\begin{minipage}{0.30\linewidth}
+\begin{minipage}{0.35\linewidth}
 \vspace{-2em}
-{	\includegraphics[width=\linewidth]{XFIG/Bisim}}
+{	\includegraphics[width=1.02\linewidth]{XFIG/Bisim}}
 \end{minipage}
@@
 
-The proof of this theorem can be found in Annex~\ref{thm-equiv-proof}. The
+The proof of this theorem can be found in \ref{thm-equiv-proof}. The
 only non-trivial part of the proof is the proof of transitivity. It
@@
 
-The definition of bisimulation for open automata allows us to derive the characterization and properties of a
+The definition of bisimulation for open automata allows us to derive  a
 bisimulation relation for open pNets. As pNets are composition
@@
   \triangleright| \forall i\in L. s_i \in S_i\}$.
-A pLTS being its own single leave:\\
+A pLTS being its own single leave:
   $States(\mylangle S,s_0,V, \to\myrangle) = \{\triangleleft s \triangleright| s \in S \}$.  
@@
 
-\subsubsection*{Predicates} 
+\paragraph{Predicates} 
 %Let
@@
 the actions of the involved sub-pNets and the resulting actions.
-
  This predicate verifies:
@@
 \\     	
-	\forall m\!\!\in\!\! I_1. {\pNet_m 
+	\forall m\!\in\! I_1.\, {\pNet_m 
 	\models\openrule
@@
   \\\\
-\forall m\!\!\in\!\! I_2.		{ \pNet_m 
+\forall m\!\in\! I_2.\,		{ \pNet_m 
     	 \models
@@
 		 Then there exist $\alpha_Q$, $\Pred\,'$, $\Pred\,''$, 
-		$\Post\,'$, $\Post\,''$ s.t.:\\[-2ex]
+		$\Post\,'$, $\Post\,''$ s.t.:\\[-.5ex]
 		%\[
@@
 \begin{thm}[Context equivalence]\label{thm-ctxt-eq}
-	Consider two  open pNets
+	Consider two  open pNets\\
 	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
@@
 	J}, 	\set{\symb{SV'}}\myrangle$ that are FH-bisimilar
-	(recall they must have the same holes to be bisimilar).
+	(they thus have the same holes).
 	Let $j_0\in J$ be a hole, and $Q$ be a pNet such that $\Sortop(Q)=\Sort_{j_0}$. Then 
@@
 This is done in a way that resembles the process of $\tau$ saturation: we add  $\tau$ open transitions before or after another (observable or not) open transition.
-\begin{definition}[Building a weak open automaton]\label{def:buildweakOT}
+\begin{definition}[Building a weak open automaton]\label{def:buildweakOT}~\\
   Let $A = \mylangle J,\mathcal{S},s_0,V,\mathcal{T}\myrangle$ be an open automaton. 
@@
 \\
+\set{\gamma}=\set{\gamma_1}\dotcup \set{\gamma_2}\subst{\Post_1}\dotcup\set{\gamma_3}\subst{\Post_2\shortodot \Post_1}\\
+\alpha'=\alpha\subst{\Post_1}\\
 \Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land \Pred_3\subst{\Post_2\shortodot\Post_1}
-\\
-\set{\gamma}=\set{\gamma_1}\dotcup \set{\gamma_2}\subst{\Post_1}\dotcup\set{\gamma_3}\subst{\Post_2\shortodot \Post_1}\\
-\alpha'=\alpha\subst{\Post_1}
 }
@@
 Finally,  applying again \WTTrois, and using the central open transition having \texttt{\nounderline{out(b\_msg,b\_ec)}}  as $\alpha$, we get the resulting weak open transition between b1 and b0 (as shown in Figure \ref{WOT2}).
-Applying the substitutions finally yields the weak transitions family $WS_7$ in Figure  \ref{SimpleProtCounter:WeakSpecOA}.
+Applying the substitutions finally yields the weak transitions family $WS_7$ in Figure~\ref{SimpleProtCounter:WeakSpecOA}.
 
@@
 
- For readability, we only give names to the  weak open transitions of \symb{SimpleProtocolImpl} in Figure \ref{SimpleProtCounter:ImplWOA2}; we detail some of these transitions below and the full list is included in Appendix \ref{Appendix:FullExample}.
+ For readability, we only give names to the  weak open transitions of \symb{SimpleProtocolImpl} in Figure \ref{SimpleProtCounter:ImplWOA2}; we detail some of these transitions below and the full list is included in  \ref{Appendix:FullExample}.
 Let us point out that the weak OT loops ($WI_1$,$WI_2$ and $W_\tau$) on state ${000}$ are also present in all other states, we did not repeat them.
@@
 
-We can now show some of the weak OTs of Figure \ref{SimpleProtCounter:ImplWOA2} (the full table is included in Appendix \ref{Appendix:FullExample}).
+We can now show some of the weak OTs of Figure \ref{SimpleProtCounter:ImplWOA2} (the full table is included in  \ref{Appendix:FullExample}).
 As we have seen above, the effect of rule $WT_3$ when a silent action have an effect on the variable $ec$ will generate an infinite family of WOTs, depending on the number of iterations through the loops.
@@
 These are however technically more complex than the ones for open automata because each hole performs a set of actions, and thus a composed transition is the composition of one transition of the top-level pNet and a sequence of transitions of the sub-pNet that fills its hole.
-They can be found as Lemmas~\ref{lem-decomposeWOT}, Lemma~\ref{lem-Weakcompose1}, and Lemma~\ref{lem-Weakcompose} in Appendix~\ref{sec:app-composition}.
+They can be found as Lemmas~\ref{lem-decomposeWOT}, Lemma~\ref{lem-Weakcompose1}, and Lemma~\ref{lem-Weakcompose} in~\ref{sec:app-composition}.
 
@@
 \end{thm}
-The proof  is detailed in Appendix \ref{app-WFH-equiv}, it follows a similar pattern as the proof that strong FH-bisimulation is an equivalence, but technical details are different, and in practice we rely on a variant of the definition of weak FH-bisimilarity; this equivalent version simulates a \emph{weak} open transition with a set of weak open transition.
+The proof  is detailed in  \ref{app-WFH-equiv}, it follows a similar pattern as the proof that strong FH-bisimulation is an equivalence, but technical details are different, and in practice we rely on a variant of the definition of weak FH-bisimilarity; this equivalent version simulates a \emph{weak} open transition with a set of weak open transition.
 The careful use of the best definition of weak FH-bisimilarity makes the proof similar to the strong FH-bisimulation case.
@@
 	$\pNet'[\pNetQ']_{j}$ are weak FH-bisimilar. This can be shown by proving the two following theorems.
-The detailed proof of these theorem can be found in Appendix~\ref{sec:app-composition}.
+The detailed proof of these theorem can be found in~\ref{sec:app-composition}.
 The proof strongly relies on the fact that weak FH-bisimulation is an equivalence, but also on the composition properties for open automata.
@@
        	This allows us to conclude, with $\Pred_{s,u} = \bigvee_{p\in P} 
-       	\Pred_{s,p}\land\Pred_{p,u}$:
-
+       	\Pred_{s,p}\land\Pred_{p,u}$:\\
       	\begin{small}     	
 $\displaystyle{\Pred_{s,u} \land \Pred_{OT}}\\
-{~}\hspace{1cm}~ \implies\!\!\! \bigvee_{p\in P} (
+{~}\hspace{.3cm} \implies\!\!\! \bigvee_{p\in P} (
 	\Pred_{s,p}\land\Pred_{p,u} \land \Pred_{OT})\\
-{~}\hspace{1cm}~ \implies\!\!\!\bigvee_{p\in P}
+{~}\hspace{.3cm} \implies\!\!\!\bigvee_{p\in P}
  \bigvee_{x\in X} \bigvee_{y\in Y}
@@
 \\
-{~}\hspace{1cm}~ \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
-\Big( \forall j. \beta_j\!=\!\beta_{jpxy}  \land \Pred_{OT_{pxy}}
-\land \alpha\!=\!\alpha_{pxy} \land
+{~} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}\!
+\Big( \forall j. \beta_j\!\!=\!\!\beta_{jpxy}  \!\land\! \Pred_{OT_{pxy}}
+\!\land \!\alpha\!=\!\alpha_{pxy} \!\land\!
 \Pred\,'_{{pxy}}\subst{\Post_{OT}\uplus\Post_{OT_{pxy}}}\Big)$
@@
  such that  $\forall x, J'=J_{x}, (s',t_x|\Pred_{s',x})\in \mathcal{R}$; 
- and  \\
-$\Pred_{s,t} \land \Pred_{OT}\!\!\implies\!\!\!
+ and  
+\begin{multline*}
+\Pred_{s,t} \land \Pred_{OT}\!\!\implies\\
 \displaystyle{\bigvee_{x\in X}
@@
      \land \alpha\!=\!\alpha_x \!\land\!  
-     \Pred_{s',x}\subst{\Post_{OT}\!\uplus\!\Post_{OT_x}}\right)}$
+     \Pred_{s',x}\subst{\Post_{OT}\!\uplus\!\Post_{OT_x}}\right)}
+\end{multline*}
 
@@
 Moreover, by using Lemma \ref{lem-rel-OT-WOT} we know that:
-\begin{mathpar}
+\begin{multline*}
     \openrule
@@
          {s_{1i} \OTarrow {\tau} s_{1(i+1)}} \in \mathcal{T}_1  \wedge
-\\{\qquad\qquad\qquad\qquad\qquad}
+\\
 \openrule
@@
          {s_{20} \OTarrow {\alpha'} s_{21}} \in \mathcal{T}_1
- \wedge
+ \wedge\\
 \forall i \in [0..m].\openrule
@@
 \bigg)
-\end{mathpar}
+\end{multline*}
 where
@@
 (s_{31},w_{c}|\Pred_{s_{31},c})\in \mathcal{R}$ and \\
- $\Pred_{s_{21},b} \land \Pred_3\implies %\\
+ \begin{multline*}
+\Pred_{s_{21},b} \land \Pred_3\implies \\
 \displaystyle{\bigvee_{c\in C}}
@@
      \land\!  
-     \Pred_{s_{31},c}\subst{\Post_3\uplus\Post_{OT_{c}}}\right)$
+     \Pred_{s_{31},c}\subst{\Post_3\uplus\Post_{OT_{c}}}\right)
+\end{multline*}
 
@@
  \bigvee_{a\in A}
-  \!\! \left( \forall j\in J_a. \vis{\beta_{1j}}\!=\!\gamma_{ja}\!  \land\! \Pred_{OT_a}\! \land\!
-     \Pred_{s_{11},a}\subst{\Post_1\uplus\Post_{OT_a}} \wedge \Pred_2\subst{\Post_1\uplus\Post_{OT_a}} \right) \hspace{-2ex}
+  \!\! \big( \forall j\in J_a. \vis{\beta_{1j}}\!=\!\gamma_{ja}\!  \land\! \Pred_{OT_a}\! \land\\
+     \Pred_{s_{11},a}\subst{\Post_1\uplus\Post_{OT_a}} \wedge \Pred_2\subst{\Post_1\uplus\Post_{OT_a}} \big) \hspace{-2ex}
 \end{multline*}
@@
  \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigodot_{i=p-1}^{0}\Post_i}, \\
-{~\hspace{2cm}}\Pred \iff \Pred\,'
+{~}\Pred \iff \Pred\,'
 		\land \!\!\bigwedge_{p=0}^n(\alpha_p\subst{\bigodot_{i=p-1}^{0}\Post_i} = \beta_p\land \Pred_p\subst{\bigodot_{i=p-1}^{0}\Post_i} ),
@@
 &
-	\!\bigwedge_{h=0}^{k'}\!\Pred_{3h}\subst{\!\! 	\bigodot_{j=h-1}^{0}\!\!\!{\Post_{3j}}\otimes{\Post_2}  \otimes\bigodot_{h=k}^{0}\!\!\Post_{1h}}\\
-\Post_Q=&\bigodot_{h=k'}^{0}\!\!\Post_{3h}\otimes\Post_2\otimes\bigodot_{j=k}^{0}\!\!\Post_{1j}
+	\!\bigwedge_{h=0}^{k'}\!\Pred_{3h}\subst{\!\! 	\bigodot_{j=h-1}^{0}\!\!\!{\Post_{3j}}\odot{\Post_2}  \odot\bigodot_{h=k}^{0}\!\!\Post_{1h}}\\
+\Post_Q=&\bigodot_{h=k'}^{0}\!\!\Post_{3h}\odot\Post_2\odot\bigodot_{j=k}^{0}\!\!\Post_{1j}
 \end{align*}
@@
 &
-{\bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\bigodot_{j=p-1}^{0}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\bigodot_{p=m_1}^{0}\!\!\Post_{1p}}}\\
-\Post=&{\bigodot_{p=m_2}^{0}\Post_{3p}\otimes\Post_2\otimes\bigodot_{j=m_1}^{0}\Post_{1j}}
+{\bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\bigodot_{j=p-1}^{0}\!\!\Post_{3j}\odot\Post_2 \odot\!\bigodot_{p=m_1}^{0}\!\!\Post_{1p}}}\\
+\Post=&{\bigodot_{p=m_2}^{0}\Post_{3p}\odot\Post_2\odot\bigodot_{j=m_1}^{0}\Post_{1j}}
 \end{align*}

### 2022-04-01 2021-Refinement/paper/refinementarticle.tex
restructuration

@@
 \smallskip
-Consider any transition $t_{13}$ in $A_{13}$,  $t_{13}$ is obtained (by case analysis on the definition of composition) 
+
+Consider any transition $t_{13}$ in $A_{13}$.
+Based on  the definition of composition $t_{13}$ can be obtained from two different cases, we will consider the two cases separately.
+$t_{13}$ is obtained
 \begin{enumerate}
@@
 \OT{ s^1_3}{{s^1_3}'}{\alpha_3^1}{   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{ g^1_3 }{ \psi^1_3} \qquad \text{ when } k \in J'_{1} 
-\]. We obtain:
+\] We get:
 %%%% Attention deactiver ici
@@
 \right)^{x\in X}\]
-Recall that in this case  $k \in J'_{1}$
-\item  or by  the transition $t_1=\OTx{1}{}{1}{1}$ alone with the state $s^1_3$ unchanged, if $k \not\in J_1'$
-\[t_{13} = \OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, s^1_3}}{\alpha_1}{\beta_{1j}^{j \in J'_1}}{g_1}{\psi_1}
-\]
-We then obtain a family of OTs by the simulation of $A_1$ by $A_2$ (stated above).
-As  $k \in H$ we have $k \not\in J'_{2x}$ and we build:
-\[t_{23x} = \left(
-\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, s^2_3}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x}}}{g_{2x}}{\psi_{2x}} \right)^{x\in X}\]
-
-\end{enumerate}
-
-These two cases define (depending on how $t_{13}$ is built) the family $t_{23x}$ of OTs we are looking for.
-Thus, for both cases we have to prove the following:
-\begin{align*}		
-		&\mpar{\forall x \in X, J'_{23x} \cap H' =
- J'_{13} \cap H'} \text{ and }\\
-		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ & R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
-			\nwedge g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
-		\end{array}} 
-	\end{align*}
-For all $x \in X$ we have to consider both  cases:
-\begin{align*}
-	\text{if } k \in J'_1:\quad &  J'_{23x} \cap H'  
-=((J'_{2x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{3} ) \cap (H\uplus J_3 \setminus\{k\} )\\
+Recall that in this case  $k \in J'_{1}$, so $\forall x \in X$ we have
+\begin{align*}
+  J'_{23x} \cap H'  
+&=((J'_{2x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{3} ) \cap (H\uplus J_3 \setminus\{k\} )\\
 &=((J'_{2x}\cap (H\uplus J_3))\uplus (J^{2 \prime}_{3}\cap (H\uplus J_3)))\setminus \mbrc{k}\\
@@
 		& = \mpar{(J'_1  \uplus J^{1 \prime}_{3})\setminus \mbrc{k}} \cap \mpar{(J_{3} \uplus H) \setminus \mbrc{k}}\\
-		& = J'_{13} \cap H'\\
-\text{if } k \notin J'_1:\quad &	J'_{23x} \cap H'  = J'_{2x}  \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
-& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
-& = \mpar{J'_1\cap H } \text{ since } J'_1 \cap H = J'_{2x} \cap H\\
-& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'
-\end{align*}
-For the rest of the formula we will also consider the two cases separately. 
-\begin{itemize}
-\item if $k \in J'_1$:\\
+		& = J'_{13} \cap H'
+\end{align*}
+
 The proof is based on the following facts: (i) Because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.
@@
 
-\item if $k \notin J'_1$:\\
-The proof of this case follows the same steps as the previous case the only argument that changes is that by composition we obtain:  $g_{13} \Leftrightarrow g_1$ and
+\item  or by  the transition $t_1=\OTx{1}{}{1}{1}$ alone with the state $s^1_3$ unchanged, if $k \not\in J_1'$
+\[t_{13} = \OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, s^1_3}}{\alpha_1}{\beta_{1j}^{j \in J'_1}}{g_1}{\psi_1}
+\]
+We then obtain a family of OTs by the simulation of $A_1$ by $A_2$ (stated above).
+As  $k \in H$ we have $k \not\in J'_{2x}$ and we build:
+\[t_{23x} = \left(
+\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, s^2_3}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x}}}{g_{2x}}{\psi_{2x}} \right)^{x\in X}\]
+
+\end{enumerate}
+
+These two cases define (depending on how $t_{13}$ is built) the family $t_{23x}$ of OTs we are looking for.
+Thus, for both cases we have to prove the following:
+\begin{align*}		
+		&\mpar{\forall x \in X, J'_{23x} \cap H' =
+ J'_{13} \cap H'} \text{ and }\\
+		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ & R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
+			\nwedge g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
+		\end{array}} 
+	\end{align*}
+
+Recall this case $k \notin J'_1$, $\forall x \in X$ we have
+\begin{align*}		
+J'_{23x} \cap H' & = J'_{2x}  \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
+& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
+& = \mpar{J'_1\cap H } \text{ since } J'_1 \cap H = J'_{2x} \cap H\\
+& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'
+\end{align*}
+
+The proof of the rest of the formula follows the same steps as the previous case the only argument that changes is that by composition we obtain:  $g_{13} \Leftrightarrow g_1$ and
 $g_{23x}  \Leftrightarrow g_{2x}$.
- \end{itemize}
+
 \item The last formula we need to prove is the following: for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
@@
 Consider any transition $t_{12}$ in $A_{12}$,  $t_{12}$ is obtained (by case analysis on the definition of composition)
+
 \begin{enumerate}
@@
 \OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{   {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1} \qquad \text{ when } k \in {J^1_{1}}^{\prime}
-\]. We obtain:
-%%%% Attention deactiver ici
+\]
+ We obtain:
 \[
@@
 Recall that in this case  $k \in {J^1_{1}}^{\prime}$
-
-\item  or by  the transition $t_1^1=
-\OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{{(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1}$  alone with the state $s_2$ unchanged, if $k \not\in {J^1_{1}}^{\prime}$
-\[t_{12} = \OT{\mpar{s^1_1, s_2}}{\mpar{{s^1_1}', s_2}}{\alpha_1^1}{ {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{g^1_1}{\psi^1_1}
-\]
-We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (stated above).
-As  $k \in H$ we have $k \not\in J'_{3x}$ and we build with the same transitions of $A_1$ (up renaming):
-\[t_{13x} = \left(\OT{\mpar{s^2_1, s_3}}{\mpar{{s^2_1}', s_{3}}}{\alpha_1^2}{ {(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{g^2_1}{\psi^2_1} \right)^{x\in X}\]
-\end{enumerate}
-We have to  prove the following formula in both cases (depending on how the transition $t_{12}$ is built): $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$ and
-\begin{multline*}	
-V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \wedge\\[12pt]
-			 g_{13x} \wedge R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
-		\end{array}} 
-	\end{multline*}
-For all $x \in X$ we have to consider both  cases:
-\begin{align*}
-	\text{if } k \in {J^1_{1}}^{\prime}:\quad &  J'_{13} \cap H'  
-=((J^{2 \prime}_{1} \uplus J'_{3x}) \setminus \mbrc{k}) \cap ((H\uplus J_1) \setminus\{k\} )\\
+\begin{align*}
+J'_{13} \cap H'  
+&=((J^{2 \prime}_{1} \uplus J'_{3x}) \setminus \mbrc{k}) \cap ((H\uplus J_1) \setminus\{k\} )\\
 & =((J^{2 \prime}_{1} \cap (H\uplus J_1)) \uplus (J'_{3x} \cap  (H\uplus J_1)))\setminus \mbrc{k}\\
@@
 & = J'_{12}\cap H'\\
-\text{if } k \notin {J^1_{1}}^{\prime}:\quad &	J'_{13x} \cap H'  = J'_{3x}  \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \\
-& = \mpar{J'_{3x}\cap H } \text{ since } J'_{3x}\cap J_1=\emptyset \land k\not\in J'_{3x} \\
-& = \mpar{J'_2\cap H } \text{ since } J'_2 \cap H = J'_{3x} \cap H\\
-& = \mpar{J'_{12}\cap H' } \text{ since } J_2\cap J'_1=\emptyset \land k\not\in {J^1_{1}}^{\prime}
-\end{align*}
-For the rest of the formula we will also consider the two cases separately. 
-\begin{itemize}
-\item if $k \in {J^1_{1}}^{\prime}$:\\
+\end{align*}
+
+if $k \in {J^1_{1}}^{\prime}$:\\
 As before, the proof  is based  on the fact that the composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.
@@
 	\end{multline*}
+
+\item  or by  the transition $t_1^1=
+\OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{{(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1}$  alone with the state $s_2$ unchanged, if $k \not\in {J^1_{1}}^{\prime}$
+\[t_{12} = \OT{\mpar{s^1_1, s_2}}{\mpar{{s^1_1}', s_2}}{\alpha_1^1}{ {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{g^1_1}{\psi^1_1}
+\]
+We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (stated above).
+As  $k \in H$ we have $k \not\in J'_{3x}$ and we build with the same transitions of $A_1$ (up renaming):
+\[t_{13x} = \left(\OT{\mpar{s^2_1, s_3}}{\mpar{{s^2_1}', s_{3}}}{\alpha_1^2}{ {(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{g^2_1}{\psi^2_1} \right)^{x\in X}\]
+\end{enumerate}
+We have to  prove the following formula in both cases (depending on how the transition $t_{12}$ is built): $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$ and
+\begin{multline*}	
+V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \wedge\\[12pt]
+			 g_{13x} \wedge R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
+		\end{array}} 
+	\end{multline*}
+For all $x \in X$ we have to consider both  cases:
+\begin{align*}
+\text{if } k \notin {J^1_{1}}^{\prime}:\quad &	J'_{13x} \cap H'  = J'_{3x}  \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \\
+& = \mpar{J'_{3x}\cap H } \text{ since } J'_{3x}\cap J_1=\emptyset \land k\not\in J'_{3x} \\
+& = \mpar{J'_2\cap H } \text{ since } J'_2 \cap H = J'_{3x} \cap H\\
+& = \mpar{J'_{12}\cap H' } \text{ since } J_2\cap J'_1=\emptyset \land k\not\in {J^1_{1}}^{\prime}
+\end{align*}
+
+	\begin{itemize}
+
 \item if $k \notin J^{1\prime}_1$:\\

### 2022-04-05 2021-Refinement/paper/refinementarticle.tex
proof restructuree fin

@@
 Based on  the definition of composition $t_{13}$ can be obtained from two different cases, we will consider the two cases separately.
-$t_{13}$ is obtained
+Namely, $t_{13}$ is obtained
 \begin{enumerate}
-\item either by the composition of a transition $t_1=\OTx{1}{}{1}{1}$ and a transition \[t_3^1=
+\item either by the composition of  transitions $t_1=\OTx{1}{}{1}{1}$ and  \[t_3^1=
 \OT{ s^1_3}{{s^1_3}'}{\alpha_3^1}{   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{ g^1_3 }{ \psi^1_3} \qquad \text{ when } k \in J'_{1} 
-\] We get:
+\] The result is:
 %%%% Attention deactiver ici
@@
 \]
-We then obtain a family of OTs by the simulation of $A_1$ by $A_2$ (stated above).
+We then obtain a family of OTs by the simulation of $A_1$ by $A_2$ (as stated above).
 By hypothesis we have $k \in H$, so in the case where $k \in J'_{1}$, we deduce that $k \in J'_{2x}$ we can  then build  a family of OTs $t_{23x}^{x\in X}$ with the same transitions of $A_3$ (up to renaming) as those used to build $t_{13}$.
@@
 
-The proof is based on the following facts: (i) Because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.
+In this case the composition gives: \[g_{13} \Leftrightarrow g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k} \text{ and }
+g_{23x}  \Leftrightarrow g_{2x} \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk}\]
+As $k \in H$ we have   
+$\beta_{1k} = \beta_{2xk}$ then we  deduce:
+\[g^1_3 \wedge \alpha^1_3=\beta_{1k}  \Leftrightarrow g^2_3 \wedge \alpha^2_3= \beta_{2xk}\]
+The proof of the rest  is based on the following facts: 
+\begin{enumerate}
+\item  Because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.
 By construction of  $t_{13}$ and $t_{23}$ we have $\alpha_{13}=
@@
 $\alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$.
-(ii) We have: \\ $\beta_{13j}^{j\in J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
+\item By composition we have also: \\ $\beta_{13j}^{j\in J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
 and $\beta_{23xj}^{j\in J'_{23}}= \beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }$\\
 Therefore, we have for all $j\in J'_{13}$ (recall that $J'_{13}=J'_{23}$):  \[\beta_{13j} = \beta_{23xj} \Rightarrow (j\in J_1 \land \beta_{1j} = \beta_{2xj}) \vee (j\in J_3^1 \land \beta^1_{3j}= \beta^2_{3j})\]
-(iii) Considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up to renaming)  we have: 
-${\displaystyle V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}} \vdash \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$
-
-And suppose that  $V_{1} \uplus V_{2} \uplus \fvars{t_1}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}}$ holds then we can deduce:
+\item 
+Considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up to renaming)  we have: 
+${\displaystyle V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}} \vdash \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$\\
+The disjunction with the following hypothesis:\\ $V_{1} \uplus V_{2} \uplus \fvars{t_1}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}}$  will give:
 \begin{align*}
@@
 \end{align*}
-Finally, the composition gives $g_{13} \Leftrightarrow g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}$ and
-$g_{23x}  \Leftrightarrow g_{2x} \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk}$. \\
-Furthermore, as $k \in H$ we have   
-$\beta_{1k} = \beta_{2xk}$ then we  deduce:
-$g^1_3 \wedge \alpha^1_3=\beta_{1k}  \Leftrightarrow g^2_3 \wedge \alpha^2_3= \beta_{2xk}$
-
-From all the implications induced by the extension of the valuation context mentioned above in the formula $(*)$ and by using the results (i), (ii) and (iii), we get:
+\end{enumerate}
+
+By the extension of the valuation context mentioned above in the formula $(*)$ and by using the results (i), (ii) and (iii), we get:
 \begin{multline*}
@@
 
-Recall this case $k \notin J'_1$, $\forall x \in X$ we have
+Recall in this case $k \notin J'_1$, $\forall x \in X$ we have
 \begin{align*}		
@@
 \begin{enumerate}
-\item either by the composition of a transition $t_2=\OTx{2}{}{2}{2}$ and a transition \[t_1^1=
+\item either by the composition of transitions $t_2=\OTx{2}{}{2}{2}$ and  \[t_1^1=
 \OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{   {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1} \qquad \text{ when } k \in {J^1_{1}}^{\prime}
 \]
- We obtain:
+The result is the transition:
 \[
@@
 & = ((J'_{2} \uplus J^{1 \prime}_{1})\setminus \mbrc{k}) \cap   ((J_1 \uplus H)\setminus \mbrc{k})\\
-& = J'_{12}\cap H'\\
-\end{align*}
-
-if $k \in {J^1_{1}}^{\prime}$:\\
-As before, the proof  is based  on the fact that the composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.
-(i)  By construction of  $t_{12}$ and $t_{13}$ we have $\alpha_{12}=
+& = J'_{12}\cap H'
+\end{align*}
+In this case the composition gives:
+\[g_{12} \Leftrightarrow g^1_1 \wedge g_2 \wedge \alpha_2=\beta^1_{1k} \text{ and } g_{13x}  \Leftrightarrow g^2_1 \wedge  g_{3x}  \wedge \alpha_{3x}=\beta^2_{1k}\] 
+Furthermore, as $\beta^1_{1k} = \beta^2_{1k}$ then we get:
+\[ g^1_1  \wedge \alpha_2=\beta^1_{1k}  \Leftrightarrow g^2_1  \wedge \alpha_{3x}=\beta^2_{1k}\]
+As the previous case, the rest of the proof is based  on the fact:
+\begin{enumerate}
+\item The composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.
+By construction of  $t_{12}$ and $t_{13}$ we have $\alpha_{12}=
 \alpha^1_{1}$ and $\alpha_{13x}=\alpha^2_{1}$. As  $\alpha^1_{1}=\alpha^2_{1}$  we deduce: 
-$\alpha_{12} = \alpha_{13x}$. (ii) In addition we have:\\
+$\alpha_{12} = \alpha_{13x}$. 
+\item By composition we have also:\\
  $\beta_{12j}^{j\in J'_{12}}= {({\beta^1_{1j}})^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {\beta_{2j}^{j \in J^{\prime}_2} }}$ and $\beta_{13xj}^{j\in J'_{13}}= {{(\beta^2_{1j})^{j \in {J^{2 \prime}_1} \setminus \{k\}}}\uplus \beta_{3xj}^{j \in J'_{3x} } }$
@@
 \[\beta_{12j} = \beta_{13xj} \Rightarrow (j\in J^{1 \prime}_1 \land \beta^1_{1j}= \beta^2_{1j}) \vee  (j\in J'_2 \land \beta_{2j} = \beta_{3xj})  \]
-(iii) Considering $\beta^1_{1j}$ and  $\beta^2_{1j}$  are the same (up to renaming)  we have: 
+
+\item And considering $\beta^1_{1j}$ and  $\beta^2_{1j}$  are the same (up to renaming)  we have: 
 ${\displaystyle V^1_{1} \uplus V^2_{1} \uplus \fvars{t_{1}} \vdash \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1\implies \bigwedge_\subbox{j \in J^{\prime}_1} \beta^1_{1j}= \beta^2_{1j}}$.
@@
 \end{align*}
-Moreover, from the composition we deduce:
-$g_{12} \Leftrightarrow g^1_1 \wedge g_2 \wedge \alpha_2=\beta^1_{1k}$ and $g_{13x}  \Leftrightarrow g^2_1 \wedge  g_{3x}  \wedge \alpha_{3x}=\beta^2_{1k}$. 
-Furthermore, as    
-$\beta^1_{1k} = \beta^2_{1k}$ then we  deduce:
-$ g^1_1  \wedge \alpha_2=\beta^1_{1k}  \Leftrightarrow g^2_1  \wedge \alpha_{3x}=\beta^2_{1k}$.
-
+\end{enumerate}
 From the results (i), (ii), (iii)  and the formula $(*)$ we get:
@@
 	\end{multline*}
-For all $x \in X$ we have to consider both  cases:
-\begin{align*}
-\text{if } k \notin {J^1_{1}}^{\prime}:\quad &	J'_{13x} \cap H'  = J'_{3x}  \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \\
+Recall in this case  $k \notin {J^1_{1}}^{\prime}$, so for all $x \in X$ we have:
+\begin{align*}
+	J'_{13x} \cap H' & = J'_{3x}  \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \\
 & = \mpar{J'_{3x}\cap H } \text{ since } J'_{3x}\cap J_1=\emptyset \land k\not\in J'_{3x} \\
@@
 \end{align*}
-
-	\begin{itemize}
-
-\item if $k \notin J^{1\prime}_1$:\\
 The proof of this case follows the same steps as the previous case the only argument that changes is that by composition we obtain:  $g_{12} \Leftrightarrow g^1_1$ and
 $g_{13x}  \Leftrightarrow g^1_{2}$.
-	\end{itemize}
 

### 2022-04-07 2016-Weak-FH-Bisim/Coverletter.tex
cover letter and proof structure

@@
 \section*{Cover Letter }
-\subsection*{Submission to Logical Methods in Computer Science}
+\subsection*{Submission to Journal of Logical and Algebraic Methods in Programming}
 \medskip
@@
 \medskip
-This article defines bisimulation relations  for the comparison of systems specified as parameterised Networks of synchronised automata; it formalises the work we did in the last 4 years and provides a theory for the operators composing concurrent processes.
+This article defines bisimulation relations  for the comparison of systems specified as parameterised Networks of synchronised automata (called pNets); it formalises the work we did in the last 4 years and provides a theory for the operators composing concurrent processes.
 This theory is based on the definition of operators as open processes.
@@
 Behavioural equivalences for pNets, like strong and weak bisimilarities, are defined over such a open transition systems.
-We finally prove that these equivalences are c
-ompositional.
+We finally prove that these equivalences are compositional.
 
@@
 
-We think this article fits with the scope and criteria of ``Logical Methods in Computer Science'' for the following reasons.
+We think this article fits with the scope and criteria of ``Journal of Logical and Algebraic Methods in Programming'' for the following reasons.
 First, to our knowledge this is the first paper proposing a theoretical framework for analysing the behaviour of open systems modeled as pNets, i.e., open terms of suitable process calculi.
-Second, the quite theoretical and fundamental approach adopted in this paper fits well to the topics of LMCS.
-Finally, because we already applied pNets and their equivalence relations to the verification of concrete cases and because we illustrate our approach on a small but realistic example, we believe our article illustrates well the applicability of the theory we propose.
+Second, the quite theoretical and fundamental approach adopted in this paper fits well to the topics of JLAMP.
+Also, we believe our article illustrates well the applicability of the theory we propose.
+Finally, the semantics of closed pNets and their usage was published in JLAMP in 2017; this submission extends the previous work to open systems and consequently provides a more symbolic semantics.
 
@@
 
-Considering the length of the submitted material,
- we   suggest to
-keep the two first appendices in the final version of the paper (leading to a
-paper of 66 pages)  because they are important to understand the paper and contain the proofs.
-The other appendix  will be available as a research report, we keep
-them in the submission to ease the work of the reviewers. 
-Of course, depending on the opinion of the reviewers, we could also move more material to  the body of the paper, or remove more proofs from the published version and only keep them in the report for example.
-
-\smallskip
-
-Finally, after a brief exchange with Alexandra Silva, we improved the form of the paper as follows.
-We improved the spacings at some places (e.g.
-between superscripts and rest of text) and tracked overfull boxes.
-We also adopted a reduced number of symbols and tried to reduce the use of $<....>$ to the synchronisation vectors where this notation is usual now.
+Considering the length of the submitted material, the article is 40 pages long but with 50 pages of appendices.
+The first 2 appendices (approx.
+35 pages) are detailed proofs, and the last one (approx 15 pages) is details on the usecase.
+Depending on the policy of the journal concerning paper length and on the opinion of the reviewers we could either publish only the body of the paper, or keep the two first appendices, or keep the 90 pages.
+In any case, all appendices will appear in a research report.
 

### 2022-04-07 2016-Weak-FH-Bisim/WeakBisim.tex
cover letter and proof structure

@@
 \begin{align*}
-\Pred\,''&=\Big(\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}}\land%\\ &\qquad
+\Pred\,''&=\Big(\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}}\\ &\qquad\qquad \land
 %~\quad
@@
 \land \bigwedge_{t=0}^{n} \Pred_t\bigodot_{i=t-1}^{0}\!\!\Post_i%\\&\qquad
-\land \Big( \bigwedge_{i=0}^{m-1}(\beta_{1{n_i}{j_0}}=\alpha_i)\subst{\bigodot_{j={n_i}-1}^{0}\Post\,'_{1j}}\land(\beta_{2{j_0}}=\alpha_m) \subst{\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}}\land\\ &\qquad
-~\quad\bigwedge_{i=m+1}^{n}(\beta_{3{n'_i}{j_0}}=\alpha_i)\subst{\bigodot_{j=n'_i-1}^{0}\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}}\Big)\displaybreak[0]\\
+\land \Big( \bigwedge_{i=0}^{m-1}(\beta_{1{n_i}{j_0}}=\alpha_i)\subst{\bigodot_{j={n_i}-1}^{0}\Post\,'_{1j}}\land(\beta_{2{j_0}}=\alpha_m) \subst{\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}}\\ &\qquad
+~\quad\land\bigwedge_{i=m+1}^{n}(\beta_{3{n'_i}{j_0}}=\alpha_i)\subst{\bigodot_{j=n'_i-1}^{0}\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}}\Big)\displaybreak[0]\\
 &=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\!\!\bigodot_{j=p-1}^{0}\!\!\Post_{1j}}\big)\land\Pred_2\subst{\!\!\bigodot_{p=m_1}^{0}\!\!\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\!\bigodot_{j=p-1}^{0}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\!\bigodot_{p=m_1}^{0}\!\!\Post_{1p}}\Big)\\&\qquad
 \land \bigwedge_{t=0}^{n} \Pred_t\bigodot_{i=t-1}^{0}\!\!\Post_i
-\land \Big(\bigwedge_{i=0}^{m-1}(\beta_{i}=\alpha_i)\subst{\bigodot_{j={i-1}}^{0}\!\!\Post_{j}}\land(\beta_m=\alpha_m )\subst{\bigodot_{j=m}^{0}\Post_{j}}\land\\ &\qquad
-~\quad\bigwedge_{i=m+1}^{n}(\beta_i=\alpha_i)\subst{\bigodot_{j=i-1}^{m}\!\!\Post_j\shortodot\Post_m\shortodot\bigodot_{j=m-1}^{0}\!\!\Post_{j}}\Big)\\
+\land \Big(\bigwedge_{i=0}^{m-1}(\beta_{i}=\alpha_i)\subst{\bigodot_{j={i-1}}^{0}\!\!\Post_{j}}\land(\beta_m=\alpha_m )\subst{\bigodot_{j=m}^{0}\Post_{j}}\\ &\qquad
+~\quad\land\bigwedge_{i=m+1}^{n}(\beta_i=\alpha_i)\subst{\bigodot_{j=i-1}^{m}\!\!\Post_j\shortodot\Post_m\shortodot\bigodot_{j=m-1}^{0}\!\!\Post_{j}}\Big)\\
 &=\Pred
@@
 Consider the first triple <b0, 000, True>, we have to prove the following 6 properties, in which $OT<<WOT$ means that the (strong) open transition $OT$ is covered, in the sense
-of definition \ref{def-Weak-bisim}, by the weak transition $WOT$ (it could be a set, but this will not be used here):
+of Definition \ref{def-Weak-bisim}, by the weak transition $WOT$ (it could be a set, but this will not be used here):
 

### 2022-04-07 2021-Refinement/paper/refinementarticle.tex
cover letter and proof structure

@@
 
-Consider any transition $t_{13}$ in $A_{13}$.
-Based on  the definition of composition $t_{13}$ can be obtained from two different cases, we will consider the two cases separately.
-Namely, $t_{13}$ is obtained
-\begin{enumerate}
-\item either by the composition of  transitions $t_1=\OTx{1}{}{1}{1}$ and  \[t_3^1=
+Consider any transition $t_{13}$ in $A_{13}$.  Based on  the definition of composition $t_{13}$ can be obtained from two different cases, we will consider the two cases separately. 
+%\begin{enumerate}
+%\item 
+\paragraph{First case: Both automata perform a transition}
+ $t_{13}$ is obtained by the composition of  transitions $t_1=\OTx{1}{}{1}{1}$ and  \[t_3^1=
 \OT{ s^1_3}{{s^1_3}'}{\alpha_3^1}{   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{ g^1_3 }{ \psi^1_3} \qquad \text{ when } k \in J'_{1} 
@@
 
-\item  or by  the transition $t_1=\OTx{1}{}{1}{1}$ alone with the state $s^1_3$ unchanged, if $k \not\in J_1'$
+\smallskip
+
+\paragraph{Second case: Only the encompassing automaton performs a transition}
+ $t_{13}$ is obtained  by  the transition $t_1=\OTx{1}{}{1}{1}$ alone with the state $s^1_3$ unchanged, if $k \not\in J_1'$
 \[t_{13} = \OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, s^1_3}}{\alpha_1}{\beta_{1j}^{j \in J'_1}}{g_1}{\psi_1}
@@
 which gives us what we needed to demonstrate. \qed
- \end{enumerate}
+% \end{enumerate}
 
@@
 \smallskip
-Consider any transition $t_{12}$ in $A_{12}$,  $t_{12}$ is obtained (by case analysis on the definition of composition)
-
-\begin{enumerate}
-\item either by the composition of transitions $t_2=\OTx{2}{}{2}{2}$ and  \[t_1^1=
+Consider any transition $t_{12}$ in $A_{12}$,  $t_{12}$ is obtained (by case analysis on the definition of composition).
+
+%\begin{enumerate}
+%\item 
+\paragraph{First case: Both automata perform a transition}
+
+$t_{12}$ is obtained  by the composition of transitions $t_2=\OTx{2}{}{2}{2}$ and  \[t_1^1=
 \OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{   {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1} \qquad \text{ when } k \in {J^1_{1}}^{\prime}
@@
 
-\item  or by  the transition $t_1^1=
+\smallskip
+\paragraph{First case: Only the encompassing automaton performs a transition}~\\
+
+$t_{12}$ is obtained  by  the transition $t_1^1=
 \OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{{(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1}$  alone with the state $s_2$ unchanged, if $k \not\in {J^1_{1}}^{\prime}$
@@
 ~\qed
-\end{enumerate}
+%\end{enumerate}
 

### 2022-04-07 2021-Refinement/paper/refinementarticle.tex
accomodation

@@
 Suppose that \(k \in H\) and that \(A_1\subst{A_3}{k}\) is non-blocking.
-We have: \[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{J_3 \uplus H \setminus \mbrc{k}}\].
+We have: \[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{J_3 \uplus H \setminus \mbrc{k}}\]
 \end{theorem}
@@
 Suppose that \(k \in H\) and that \(A_1\subst{A_2}{k}\) is non-blocking.
-We have: \[\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{J_1 \uplus H \setminus \mbrc{k}}\].
+We have: \[\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{J_1 \uplus H \setminus \mbrc{k}}\]
 \end{theorem}
@@
 
+\begin{quote}
+Suppose that $\wrel{A_1}{A_2}{H}$, \(k \in H\) and that \(A_1\subst{A_3}{k}\) is non-blocking.
+We have: \[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{J_3 \uplus H \setminus \mbrc{k}}\]
+\end{quote}
+
+\TODO{The subtlety here is that the original relation implies that valuations in A3 are equal (ie the value for each variable are the same in both valuations, modulo renaming), after a transition we should obtain ``equal'' valuations because Post are deterministic}
+
 \proof
@@
 %\item 
-\paragraph{First case: Both automata perform a transition}
- $t_{13}$ is obtained by the composition of  transitions $t_1=\OTx{1}{}{1}{1}$ and  \[t_3^1=
+\paragraph{First case: Both automata perform a transition.}
+The transition $t_{13}$ is obtained by the composition of  transitions $t_1=\OTx{1}{}{1}{1}$ and  \[t_3^1=
 \OT{ s^1_3}{{s^1_3}'}{\alpha_3^1}{   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{ g^1_3 }{ \psi^1_3} \qquad \text{ when } k \in J'_{1} 
 \] The result is:
-%%%% Attention deactiver ici
 \[
@@
 \item 
-Considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up to renaming)  we have: 
+Considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up to renaming)  we have: \\
 ${\displaystyle V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}} \vdash \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$\\
@@
 
-By the extension of the valuation context mentioned above in the formula $(*)$ and by using the results (i), (ii) and (iii), we get:
+By the extension of the valuation context mentioned above in the formula $(*)$ and by using the statements resulting from the cases (a), (b) and (c), we get:
 \begin{multline*}
@@
 \end{multline*}
-\TODO{The subtlety here is that the original relation implies that valuations in A3 are equal (ie the value for each variable are the same in both valuations, modulo renaming), after a transition we should obtain ``equal'' valuations because Post are deterministic}
 
@@
 
+Suppose that $\wrel{A_2}{A_3}{H}$, \(k \in H\) and that \(A_1\subst{A_2}{k}\) is non-blocking.
+We have: \[\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{J_1 \uplus H \setminus \mbrc{k}}\]
 \proof
@@
 	\end{multline*}
-By definition of composition and open automata refinement we have: 
+By the definition of composition and open automata refinement we have: 
 \begin{align*}
@@
 %\item 
-\paragraph{First case: Both automata perform a transition}
-
-$t_{12}$ is obtained  by the composition of transitions $t_2=\OTx{2}{}{2}{2}$ and  \[t_1^1=
+\paragraph{First case: Both automata perform a transition.} ~~\\
+The transition $t_{12}$ is obtained  by the composition of transitions $t_2=\OTx{2}{}{2}{2}$ and  \[t_1^1=
 \OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{   {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1} \qquad \text{ when } k \in {J^1_{1}}^{\prime}
@@
 \end{enumerate}
-From the results (i), (ii), (iii)  and the formula $(*)$ we get:
+From the statements resulting the cases (a), (b) and (c),  and by  the formula $(*)$ we get:
 \begin{multline*}
@@
 \smallskip
-\paragraph{First case: Only the encompassing automaton performs a transition}~\\
-
-$t_{12}$ is obtained  by  the transition $t_1^1=
+\paragraph{Second case: Only the encompassing automaton performs a transition.}~\\
+The transition $t_{12}$ is obtained  by  the transition $t_1^1=
 \OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{{(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1}$  alone with the state $s_2$ unchanged, if $k \not\in {J^1_{1}}^{\prime}$

### 2022-04-12 2021-Refinement/paper/refinementarticle.tex
Submission weak bisim + work on the refinement paper (body)

@@
 With such a relation we are able to check the refinement between two open automata with the same level of abstraction but specified differently, for example, by duplicating states, removing transitions,  reinforcing  guards, modifying variables.
-However, this refinement is inappropriate in the setting of composition which is the main advantage of the open automaton-based approach. 
-\TODO{introduce somewhere refinement through composition} 
-Refinement through composition  leads to a model in which composition can be used both to add new holes to a system and to fill holes, obtaining a system with less holes.
-Next section will identify a refinement relation with the possibility to have different holes in the compared automata.
+
+ We will show in Section~\ref{sec:prop} that this refinement relation has good properties in terms of transitivity, compositionality, reflexivity, etc.
+
+The refinement relation defined above is insufficient in the setting of composition which is the main advantage of the open automaton-based approach.
+Indeed, it should be possible to refine an automaton by filling its hole, providing a concrete view of a part of the application that was not specified originally.
+More generally, it should be possible to relate automata that do not have the same holes because composition is a crucial part of system specification.
+Thus, we believe composition should also be a form of refinement and call this feature \emph{refinement through composition}.
+However, filling holes can result in a system with more or less holes than the original system because the plugged subsystem can contain itself many holes.
+Next section will define  a more powerful refinement relation able to reason on automata with different sets of holes.
 
@@
 \TODO{add an example}
-
-\TODO{refer to properties of section 6} We will show in Section~\ref{sec:prop} that this refinement relation has god properties in terms of transitivity, compositionality, reflexivity, etc.
-
-\TODO{4 pages}
 
@@
 
-Above we designed a refinement relation that compares OAs with the same holes, it ensures simulation at the automaton level, with symbolic evaluation of the guards and transitions.
-We want now to extend this to automata where the set of holes is not the same.
-A trivial use-case for this is filling a hole with a completely defined automaton.
+This section  extends the preceding relation to automata where the set of holes is not the same.
+A simple use-case for this is filling a hole with a completely defined automaton.
 In this case, we want to ensure that the automaton with a filled hole is a refinement of the other automata: actions of the identical holes will be taken into account the same way, and filling the hole partially reduces the behaviour of the automaton.
 
-The major challenge in this case is to maintain a form of transitivity while being able to take into account the actions of some of the holes.
-A naive definition of refinement would ensure that the holes that are identical in the two OAs are taken into account in the simulation.
-Unfortunately this does not work well with transitivity as if $A_1$ simulates $A_2$ and $A_2$ simulates $A_3$, and one hole appears in $A_3$ and in $A_1$ but not in $A_2$ then we have no proven property on the way $A_1$ and $A_3$ takes his hole into account, and in general  $A_1$ does not simulate $A_3$.
+The major challenge in the design of this relation is to maintain a form of transitivity while being able to take into account the actions of some of the holes.
+A naive definition of refinement would ensure that the holes that are identical in the two open automata are taken into account in the simulation.
+Unfortunately considering all the common holes does not ensure transitivity of the simulation for the following reason.
+If $A_1$ simulates $A_2$ and $A_2$ simulates $A_3$, and one hole $j$ appears in $A_3$ and in $A_1$ but not in $A_2$ then we have no guarantee on the way $A_1$ and $A_3$ take the actions of this his hole into account, thus  a refinement between and $A_1$ and $A_3$ would require conditions involving actions of the hole $j$ which cannot be ensured.
 The way we solve this issue is to remember in the simulation relation which holes have been compared.
 This way the relation is parameterized by the set of holes that belong to the two automata and are taken into account.
-In practice, when performing successive refinements, we  keep track of which holes are in common at each step of refinement.
-
-\TODO{say explicitly what is the difference in the formalisation compared to previous def}
+This way, in the example above, we would have no guarantee on actions the hole $j$ by transitivity but can state a refinement relation with guarantees on the actions of the other holes.
+
+In the following definition we add a parameter $H$ which is the set of holes tracked by the refinement relation and adapt the definition by ignoring actions of the holes that are not in $H$.
 \begin{definition}[Open automata refinement]\label{Def:OA-Refinement}
@@
 \end{definition}
-It is important to note that every action of the holes outside \(H\) is unconstrained in the related automata.
-It is easy to see that the hole-equal simulation is a particular case of open automata refinement, when  $J_1=J_2=H$.
+Note that every action of the holes outside \(H\) is unconstrained in the related automata.
 
@@
 
-\section{Properties}\label{sec:prop}
+\section{Properties of our Refinement Relations}\label{sec:prop}
 \TODO{1.5 pages}
-
-The first crucial property of  refinement  is that it is reflexive  and  transitive,  so  it  is  a  preorder on the set of open automata. This property enables stepwise refinement.
+We now  state the properties of our refinement relations, proofs of the properties can be found in the appendices.
+We express these properties in terms of open automata refinement because hole-equal simulation is a particular case of Definition~\ref{Def:OA-Refinement} when  $J_1=J_2=H$, and thus most of the properties shown here are easy to adapt to hole-equal simulation.
+
+The first crucial property of  refinement  is that it is  a  preorder on the set of open automata. This property enables stepwise refinement.
+
+\begin{theorem}[Refinement is a preorder]
+Refinement   is reflexive  and  transitive:  it  is  a  preorder on the set of open automata.
+\end{theorem}
 
 The relation  \(\wrel{}{}{H}\) is reflexive,  \(\wrel{A}{A}{H}\),  by taking $R\mpar{s_1, s_2} \mapsto \displaystyle\bigwedge_\subbox{v \in vars(s_1)} {v=v}$ to be $s_1= s_2$  and checking the above conditions (Definition \ref{Def:OA-Refinement}), we can see that the relation is indeed reflexive.
-
-\begin{theorem}[Transitivity]
-If $\wrel{A_1}{A_2}{H}$ and $\wrel{A_2}{A_3}{H'}$, then $\wrel{A_1}{A_3}{H\cap H'}$.
-\end{theorem}
-
-Appendix~\ref{sec:proof-transitivity} presents the proof.
+%
+%\begin{theorem}[Transitivity]
+%If $\wrel{A_1}{A_2}{H}$ and $\wrel{A_2}{A_3}{H'}$, then $\wrel{A_1}{A_3}{H\cap H'}$.
+%\end{theorem}
+Appendix~\ref{sec:proof-transitivity} presents the proof of transitivity.
 It is done classically by identifying the relation between $A_1$ and $A_3$ that is a refinement.
@@
 
-\TODO{find an informal introduction to the following:}
-The composition of $A_1$ and $A_3$ is a refinement of the composition of $A_2$ and $A_3$ provided $A_1$ is a refinement of $A_2$ and the hole in which we are composing inside $A_1$ and $A_2$ is tracked by the refinement relation.
-
-\begin{theorem}[Context refinement]
+The next to theorems state that refinement is compositional in the sense that it is sufficient to prove refinement for the composed automata separately to obtain a refinement relation.
+This can be split into theorems that can be trivially composed by transitivity.
+%
+%
+%The composition of $A_1$ and $A_3$ is a refinement of the composition of $A_2$ and $A_3$ provided $A_1$ is a refinement of $A_2$ and the hole in which we are composing inside $A_1$ and $A_2$ is tracked by the refinement relation.
+
+\begin{theorem}[Context refinement]\label{thm:ContextRefinement}
 Let $A_1$, $A_2$ and $A_3$ be three open automata with $\wrel{A_1}{A_2}{H}$. 
@@
 
-\begin{theorem}[Congruence]
+\begin{theorem}[Congruence]\label{thm:Congruence}
 Let $A_1$, $A_2$ and $A_3$ be three open automata with $\wrel{A_2}{A_3}{H}$. 
@@
 \end{theorem}
+
+\TODO{i did not put the global composition theorem, de we state it?}
+
 - composition is a refinement (under which condition? non-blocking composition?)
@@
 - what is the property wrt deadlocks?
-
-- congruence? a[b/j] if $a'$ refines $a$ and if $b'$ refines $b$?
 
@@
 
+ \bibliographystyle{splncs04}
+ \bibliography{biblio}
+
 \section{a recuperer si on se rend compte que c'est utile}
@@
 
-\section{Proof of Transitivity}\label{sec:proof-transitivity}
+\section{Proof of Transitivity for Refinement}\label{sec:proof-transitivity}
 \begin{quote}
@@
 
-\section{Proof of Context Refinement}
+\section{Proof of Context Refinement (Theorem~\ref{thm:ContextRefinement})}
 
@@
 
-\section{Proof of Congruence}
+\section{Proof of Congruence (Theorem~\ref{thm:Congruence})}
 
@@
 
- \bibliographystyle{splncs04}
- \bibliography{biblio}
-
 \end{document}

### 2022-04-14 2021-Refinement/paper/refinementarticleOld.tex

--- 2022-04-07 2021-Refinement/paper/refinementarticle.tex
@@
 \usepackage{tikz,mathpartir}
-\usepackage{mathtools}
+
 \usepackage{amsmath,amssymb,mathabx}
+%\usepackage{amsthm}
 %\usepackage{unicode-math}
@@
 \usepackage{nccrules}
-
 \AtBeginDocument{\renewcommand\setminus{\smallsetminus}}
@@
 proving that two implementation are equivalent, or justifying optimisations and transformations, by establishing that the
-behaviours of a modified program simulate those of to the source one.
+behaviors of a modified program simulate those of to the source one.
 
 In this article, we discuss a notion of refinement between so-called "open automata", which are symbolic
-behavioural models for communicating systems. Open automata may have "holes" modelling elements of their
-context, and can be composed by instantiation of the holes. This allows for a compositional approach for
-verification of their behaviour, essential to address proofs about large realistic systems.
+behavioral models for communicating systems. Open automata may have "holes" modeling elements of their
+context, and can be composed by instanciation of the holes. This allows for a compositional approach for
+verification of their behavior, essential to address proofs about large realistic systems.
 
@@
 
-\begin{definition}[Non-blocking composition]\label{Def:Non-blockcomp}
+\begin{definition}[Non-blocking composition]
 Let \(A_i = \OAg[i]\) with \( 0 \leq i \leq n\) be a family of open automata.
@@
 \end{multline*}		
-Adding to both sides of the implication the predicate $R_{23}\mpar{s_{2p},s_3}$ we get: 
+Adding to both sides of the implication the predicate $R_{23}\mpar{s_{2p},s_3}$ we get: \footnote{Note for the sake of readability, when we justify each step in a a proof
+we omit to rewrite the quantification over of formula which remains unchanged.}
 \begin{multline*}
@@
 
-From the  two previous cases: 
+The following  can be derived from the two previous cases: \\
 $\forall x \in X, J'_{2px} \cap H = J'_1 \cap H$ and
-$\forall y \in Y, J'_{2px} \cap H' = J'_{3pxy} \cap H'$ we conclude:
+$\forall y \in Y, J'_{2px} \cap H' = J'_{3pxy} \cap H'$ leading to the conclusion:\\
 $\forall x \in X, \forall y \in Y,  J'_1 \cap (H \cap H') = J'_{3pxy} \cap (H\cap H')$ \\
-
-In addition, by combining  formula $(**)$ and $(*)$, we get: 
-\begin{multline*}
-V_1 \uplus V_2 \uplus V_3  \uplus \fvars{t_1}\uplus \fvars{t_{2px}} \vdash\\
+By combining  formula $(**)$ in $(*)$, we get: 
+\begin{multline*}
+V_1 \uplus V_2 \uplus V_3  \uplus \fvars{t_1} \vdash\\
 R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies \hspace{4.5cm}\\\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
@@
 \end{multline*}		
-With  the rearrangement of the formula, we get:
+With the restriction of the domain and the rearrangement of the formula, we get:
 \begin{multline*}
@@
 
-Because of the domain of the substitutions of the relations, the formula can be re-written:
+Because of the domain of the substitutions of the relations, we have:
 \begin{multline*}
@@
 \end{multline*}
-The formula is valid for all $s_{2p} \in (s_{2p})^{p\in P}$.
-To build $R_{13}$ we need to rely on the disjunction of all possible paths to relate $s_1$ and $s_3$, which leads to\\ ${\displaystyle R_{13}(s_1,s_3)=\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}}$.
+This is valid for all $s_{2p} \in (s_{2p})^{p\in P}$.
+We need to rely on the disjunction of all possible paths to relate $s_1$ and $s_3$ with ${\displaystyle R_{13}(s_1,s_3)=\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}}$.
 \begin{multline*}
@@
 \end{multline*}
-Indeed, since $\psi_{2px}$ has no effect on variables of $A_1$ and $A_3$ we have:
+Since $\psi_{2px}$ has no effect on variables of $A_1$ and $A_3$, it then implies:
 \begin{align*}
@@
 Overall, we have a family of open transitions $t^{p\in P,x\in X,y\in Y}_{pxy} \subseteq T_3$ that should simulate $t_1$.
-All  combinations of elements in $P$, $X$, and $Y$ provide a set $Z$ of  open transitions.
-This allows us to get the desired conclusion, that there is a set of  open transitions indexed over $Z$:
+All  combinations of elements in $P$, $X$, and $Y$ provide a set $Z$ of weak open transitions.
+This allows us to get the desired conclusion, that there is a set of weak open transitions indexed over $Z$:
 %This provides the desired conclusion:\\
@@
 \medskip
-\item Finally, we need to prove the satisfaction of the  deadlock reducing condition.
-According to the refinement relation relating   $A_2$ and $A_3$ we have for all $\mpar{s_{2p}, s_3} \in S_2 \times S_3$:
+\item Finally, the satisfaction of the condition of deadlock reducing. According to the relation between   $A_2$ and $A_3$ we have for all $\mpar{s_{2p}, s_3} \in S_2 \times S_3$:
 \begin{multline*}
@@
 \begin{multline*}
-V_1 \uplus V_2 \uplus V_3 \uplus\biguplus_\subbox{p \in P} \fvars{t_{2p}} \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash \\
+ V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash \\
 R_{13}\mpar{s_1,s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \operatorname*{\bigsymb{\bigvee}}_{p\in P}\mpar{ R_{12}\mpar{s_1,s_{2p}}\wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}}}
@@
 \begin{multline*}
- V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{2p} \in \fOT{s_{2p}}} \fvars{t_{2p}} \vdash R_{12}\mpar{s_1, s_{2p}} \wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
+ V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{2p} \in \fOT{s_{2p}}} \fvars{t_{2p}} \vdash \left(R_{12}\mpar{s_1, s_{2p}} \wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
 \end{multline*}
@@
 \begin{multline*}
- V_1 \uplus V_2 \uplus \biguplus_{\mathclap{\substack{t_{2p} \in \fOT{s_{2p}}\\ p \in P}}} \fvars{t_{2p}} 
-\vdash \\
+ V_1 \uplus V_2 \uplus  \biguplus_\subbox{t_{2p} \in \fOT{s_{2p}}} \fvars{t_{2p}} \vdash \\
 \operatorname*{\bigsymb{\bigvee}}_{p\in P}\mpar{R_{12}\mpar{s_1, s_{2p}} \wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} }  \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
@@
 By using the fact that $R$ relates initial configurations of  $A_1$ and $A_2$, we have  the following statement:
-$\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}}$,  and based on the  fact that initial states are reachable $\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ we have 
+$\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}}$,  and relying on the  fact that initial states are reachable $\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ we have 
 \[ \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
@@
 
-Considering that initial valuations $\sigma_{03}^1$ and $\sigma_{03}^2$ associate the same values to the ``same'' variables modulo renaming, so the following holds:\\ $\left(\,\,{\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }$.
-
-Additionally, because  the domains of the substitution function are disjoint, the substitution function has an effect only on the related elements,  we get:
+Considering that initial valuations $\sigma_{03}^1$ and $\sigma_{03}^2$ associate the same values to the ``same'' variables modulo renaming, we have the tautology:\\ $\left(\,\,{\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }$.
+
+Because  the domains of the substitution function are disjoint, the substitution function has an effect only on the related elements,  we get:
 \begin{align*}
@@
 \end{align*}		
-there exists an indexed family $t_{23x}$ of OTs originating from $s_{23}$ that simulate it: 
+there exists an indexed family $t_{23x}$ of OTs originating from $s_{23}$ that simulates it: 
 \begin{align*}
@@
 	\end{align*}
-Recall that by definition of composition and open automata refinement we have: 
+By definition of composition and open automata refinement we have: 
 \begin{align*}
@@
 \end{align*}
-First of all, we have by hypothesis $\wrel{A_1}{A_2}{H}$, then for any open transition $t_1$ in $T_1$  originating from $s_1$:
+We have by hypothesis $\wrel{A_1}{A_2}{H}$, then for any open transition $t_1$ in $T_1$  originating from $s_1$:
 \begin{align*}
@@
 \smallskip
-
-Consider any transition $t_{13}$ in $A_{13}$.  Based on  the definition of composition $t_{13}$ can be obtained from two different cases, we will consider the two cases separately. 
-%\begin{enumerate}
-%\item 
-\paragraph{First case: Both automata perform a transition}
- $t_{13}$ is obtained by the composition of  transitions $t_1=\OTx{1}{}{1}{1}$ and  \[t_3^1=
+Consider any transition $t_{13}$ in $A_{13}$,  $t_{13}$ is obtained (by case analysis on the definition of composition)
+
+* either by the composition of a transition $t_1=\OTx{1}{}{1}{1}$ and a transition \[t_3^1=
 \OT{ s^1_3}{{s^1_3}'}{\alpha_3^1}{   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{ g^1_3 }{ \psi^1_3} \qquad \text{ when } k \in J'_{1} 
-\] The result is:
+\]. We obtain:
 %%%% Attention deactiver ici
@@
 \]
-We then obtain a family of OTs by the simulation of $A_1$ by $A_2$ (as stated above).
+We then obtain a family of OTs by the simulation of $A_1$ by $A_2$ (stated above).
 By hypothesis we have $k \in H$, so in the case where $k \in J'_{1}$, we deduce that $k \in J'_{2x}$ we can  then build  a family of OTs $t_{23x}^{x\in X}$ with the same transitions of $A_3$ (up to renaming) as those used to build $t_{13}$.
@@
 \right)^{x\in X}\]
-Recall that in this case  $k \in J'_{1}$, so $\forall x \in X$ we have
-\begin{align*}
-  J'_{23x} \cap H'  
-&=((J'_{2x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{3} ) \cap (H\uplus J_3 \setminus\{k\} )\\
+Recall that in this case  $k \in J'_{1}$
+
+* or by an the transition $t_1=\OTx{1}{}{1}{1}$ alone with the state $s^1_3$ unchanged, if $k \not\in J_1'$
+\[t_{13} = \OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, s^1_3}}{\alpha_1}{\beta_{1j}^{j \in J'_1}}{g_1}{\psi_1}
+\]
+We then obtain a family of OTs by the simulation of $A_1$ by $A_2$ (stated above).
+As  $k \in H$ we have $k \not\in J'_{2x}$ and we build:
+\[t_{23x} = \left(
+\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, s^2_3}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x}}}{g_{2x}}{\psi_{2x}} \right)^{x\in X}\]
+
+These two cases define (depending on how $t_{13}$ is built) the family $t_{23x}$ of OTs we are looking for.
+Thus, for both cases we have to prove the following:
+\begin{align*}		
+		&\mpar{\forall x \in X, J'_{23x} \cap H' =
+ J'_{13} \cap H'} \text{ and }\\
+		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ & R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
+			\nwedge g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
+		\end{array}} 
+	\end{align*}
+For all $x \in X$ we have to consider both  cases:
+\begin{align*}
+	\text{if } k \in J'_1:\quad &  J'_{23x} \cap H'  
+=((J'_{2x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{3} ) \cap (H\uplus J_3 \setminus\{k\} )\\
 &=((J'_{2x}\cap (H\uplus J_3))\uplus (J^{2 \prime}_{3}\cap (H\uplus J_3)))\setminus \mbrc{k}\\
@@
 & =((J'_{2x}\cap H)\uplus J^{2 \prime}_{3})\setminus \mbrc{k}\text{ since } J^{2 \prime}_{3}\subseteq J_3\\
-& =((J'_1\cap H)\uplus J^{1 \prime}_{3})\setminus \mbrc{k}\quad \text{ since } J^{1 \prime}_{3}=J^{2 \prime}_{3} \text{ and } J'_1 \cap H = J'_{2x} \cap H\\
+& =(J'_1\cap H)\uplus J^{1 \prime}_{3}\setminus \mbrc{k}\quad \text{ since } J^{1 \prime}_{3}=J^{2 \prime}_{3} \text{ and } J'_1 \cap H = J'_{2x} \cap H\\
 &= ((J'_1 \cap H) \uplus (J^{1 \prime}_{3} \cap J_3)) \setminus \mbrc{k}\text{ since } J^{1 \prime}_{3}\subseteq J_3\\ 
@@
 		& = \mpar{(J'_1  \uplus J^{1 \prime}_{3})\setminus \mbrc{k}} \cap \mpar{(J_{3} \uplus H) \setminus \mbrc{k}}\\
-		& = J'_{13} \cap H'
-\end{align*}
-
-In this case the composition gives: \[g_{13} \Leftrightarrow g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k} \text{ and }
-g_{23x}  \Leftrightarrow g_{2x} \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk}\]
-As $k \in H$ we have   
-$\beta_{1k} = \beta_{2xk}$ then we  deduce:
-\[g^1_3 \wedge \alpha^1_3=\beta_{1k}  \Leftrightarrow g^2_3 \wedge \alpha^2_3= \beta_{2xk}\]
-The proof of the rest  is based on the following facts: 
-\begin{enumerate}
-\item  Because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.
+		& = J'_{13} \cap H'\\
+\text{if } k \notin J'_1:\quad &	J'_{23x} \cap H'  = \mpar{J'_{2x} } \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
+& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
+& = \mpar{J'_1\cap H }\\
+& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'
+\end{align*}
+For the rest of the formula we will also consider the two cases separately. 
+\begin{itemize}
+\item if $k \in J'_1$:\\
+The proof is based on the following facts.
+First, because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.
 By construction of  $t_{13}$ and $t_{23}$ we have $\alpha_{13}=
 \alpha_{1}$ and $\alpha_{23x}=\alpha_{2x}$. So we deduce: 
-$\alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$.
-\item By composition we have also: \\ $\beta_{13j}^{j\in J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
+$\alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$.\\
+Second, we have: \\ $\beta_{13j}^{j\in J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
 and $\beta_{23xj}^{j\in J'_{23}}= \beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }$\\
-Therefore, we have for all $j\in J'_{13}$ (recall that $J'_{13}=J'_{23}$):  \[\beta_{13j} = \beta_{23xj} \Rightarrow (j\in J_1 \land \beta_{1j} = \beta_{2xj}) \vee (j\in J_3^1 \land \beta^1_{3j}= \beta^2_{3j})\]
-\item 
-Considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up to renaming)  we have: 
-${\displaystyle V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}} \vdash \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$\\
-The disjunction with the following hypothesis:\\ $V_{1} \uplus V_{2} \uplus \fvars{t_1}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}}$  will give:
+Therefore, we have for all $j\in J'_{13}$ (recall that $J'_{13}=J'_{23}$):  \[\beta_{13j} = \beta_{23xj} \Rightarrow (j\in J_1 \land \beta_{1j} = \beta_{2xj}) \vee (j\in J_3^1 \land \beta^1_{3j}= \beta^2_{3j})\]\\
+Third, considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up to renaming)  we have: 
+${\displaystyle V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}} \vdash \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$
+
+And suppose that  $V_{1} \uplus V_{2} \uplus \fvars{t_1}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}}$ holds then we can deduce:
 \begin{align*}
@@
 \end{align*}
-\end{enumerate}
-
-By the extension of the valuation context mentioned above in the formula $(*)$ and by using the results (i), (ii) and (iii), we get:
+Finally, the composition gives $g_{13} \Leftrightarrow g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}$ and
+$g_{23x}  \Leftrightarrow g_{2x} \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk}$. \\
+Furthermore, as $k \in H$ we have   
+$\beta_{1k} = \beta_{2xk}$ then we  deduce:
+$g^1_3 \wedge \alpha^1_3=\beta_{1k}  \Leftrightarrow g^2_3 \wedge \alpha^2_3= \beta_{2xk}$
+
+From all the implications induced by the extension of the valuation context mentioned above, and by entering   all previous intermediate results in the formula $(*)$, we get:
 \begin{multline*}
@@
 
-Moreover, we have  for any transition $t_3$ in $A_3$ relying $s_3$ and $s^{\prime}_3$ the following:
+We can deduce for any transition $t_3$ in $A_3$ relying $s_3$ and $s^{\prime}_3$ we have:
 \begin{multline*}
@@
  \end{multline*}	
-From the two previous formulas, we get:
+Therefore, we get:
 \begin{multline*}
@@
 			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\land\\
-			  R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge
+			 \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
  \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3) \wedge s^{1\prime}_3 = s^{2\prime}_3
@@
 \end{multline*}
-And finally by hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,   by definition of reachability (Definition \ref{Def:Reach}) we obtain $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
+And finally By hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
 \[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
@@
 \begin{multline*}
-V_{13} \uplus V_{23} \uplus  \fvars{t_{13}} \vdash\\
+V_{13} \uplus V_{23} \uplus \fvars{t_1}  \cap \fvars{t_{13}} \vdash\\
 R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \reach{A_{13}}\mpar{s_{13}}
@@
 \end{multline*}	
-Because of the independence of the substitution domains, we simplify and get the expected formula:
+Because of the independence of the substitution domains, we get the expected formula:
 	\begin{multline*}
@@
 
-\smallskip
-
-\paragraph{Second case: Only the encompassing automaton performs a transition}
- $t_{13}$ is obtained  by  the transition $t_1=\OTx{1}{}{1}{1}$ alone with the state $s^1_3$ unchanged, if $k \not\in J_1'$
-\[t_{13} = \OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, s^1_3}}{\alpha_1}{\beta_{1j}^{j \in J'_1}}{g_1}{\psi_1}
-\]
-We then obtain a family of OTs by the simulation of $A_1$ by $A_2$ (stated above).
-As  $k \in H$ we have $k \not\in J'_{2x}$ and we build:
-\[t_{23x} = \left(
-\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, s^2_3}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x}}}{g_{2x}}{\psi_{2x}} \right)^{x\in X}\]
-
+\item if $k \notin J'_1$:\\
+The proof of this case follows the same steps as the previous case the only argument that changes is that  $g_{13} \Leftrightarrow g_1$ and
+$g_{23x}  \Leftrightarrow g_{2x}$.
+ \end{itemize}
+\item The last formula we need to prove is the following: for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
+\begin{multline*}
+V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_{23}} \vdash \\ \left(R^{\prime}\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_1 \in \fOT{s_{13}}} \fguard{t_{13}} \right)
+\end{multline*}
+Let's start  with the hypothesis of the theorem stating that $\wrel{A_1}{A_2}{H}$, thus we have for all  $\mpar{s_1, s_2} \in S_1 \times S_2$ 
+\begin{multline*}
+V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
+\end{multline*}
+We have a second hypothesis stating that the result of the composition \(A_1\subst{A_3}{k}\) is non-blocking, which leads to:
+\begin{multline*}
+V_{13}  \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \left( \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \right)
+\end{multline*}
+We use the the first, we extend the valuation to cover the variables of  $t^2_3$ in $t_{23}$ using their value in $t_3$ and because $\fvars{t_{13}} \vdash \reach{A_{13}}\mpar{s_{13}}$, we get:
+\begin{multline*}
+V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}  \wedge \reach{A_{13}}\mpar{s_{13}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}   \wedge \reach{A_{13}}\mpar{s_{13}}\right)
+\end{multline*}
+By transitivity with the second hypothesis we obtain:
+\begin{multline*}
+V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}   \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}\right)
+\end{multline*}
+That implies:
+\begin{multline*}
+V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(\underbrace{R\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3}_{R^{\prime}(s_{13},s_{23})}  \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}   \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}\right)
+\end{multline*}
+which gives us what we needed to demonstrate. \qed
  \end{enumerate}
-
-These two cases define (depending on how $t_{13}$ is built) the family $t_{23x}$ of OTs we are looking for.
-Thus, for both cases we have to prove the following:
-\begin{align*}		
-		&\mpar{\forall x \in X, J'_{23x} \cap H' =
- J'_{13} \cap H'} \text{ and }\\
-		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ & R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
-			\nwedge g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
-		\end{array}} 
-	\end{align*}
-
-Recall in this case $k \notin J'_1$, $\forall x \in X$ we have
-\begin{align*}		
-J'_{23x} \cap H' & = J'_{2x}  \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
-& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
-& = \mpar{J'_1\cap H } \text{ since } J'_1 \cap H = J'_{2x} \cap H\\
-& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'
-\end{align*}
-
-The proof of the rest of the formula follows the same steps as the previous case the only argument that changes is that by composition we obtain:  $g_{13} \Leftrightarrow g_1$ and
-$g_{23x}  \Leftrightarrow g_{2x}$.
-
-\item The last formula we need to prove is the following: for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
-\begin{multline*}
-V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_{23}} \vdash \\ \left(R^{\prime}\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_1 \in \fOT{s_{13}}} \fguard{t_{13}} \right)
-\end{multline*}
-Let's start  with the hypothesis of the theorem stating that $\wrel{A_1}{A_2}{H}$, thus we have for all  $\mpar{s_1, s_2} \in S_1 \times S_2$ 
-\begin{multline*}
-V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
-\end{multline*}
-We extend the valuation to cover the variables of  $t^2_3$ in $t_{23}$ and using their value in $t_3$ and because the following statement holds: $\fvars{t_{13}} \vdash \reach{A_{13}}\mpar{s_{13}}$, we get:
-\begin{multline*}
-V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}  \wedge \reach{A_{13}}\mpar{s_{13}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}   \wedge \reach{A_{13}}\mpar{s_{13}}\right)
-\end{multline*}
-We have a second hypothesis stating that the result of the composition \(A_1\subst{A_3}{k}\) is non-blocking, by Definition \ref{Def:Non-blockcomp} we have:
-\begin{multline*}
-V_{13}  \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \left( \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \right)
-\end{multline*}
-By transitivity  we obtain:
-\begin{multline*}
-V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}   \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}\right)
-\end{multline*}
-
-Considering that each valuations $\sigma_{3}^1$ and $\sigma_{3}^2$ associate the same values to the ``same'' variables modulo renaming, so the following holds:\\ $\left(\,\,{\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{3}^1 \uplus \sigma_{3}^2 }$, we obtain:
-\begin{multline*}
-V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(\underbrace{R\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3}_{R^{\prime}(s_{13},s_{23})}  \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}   \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}\right)
-\end{multline*}
-which gives us what we needed to demonstrate. \qed
-% \end{enumerate}
 
@@
 $A_1\subst{A_3}{k}$),  to prove the theorem it is sufficient to prove that there exists a relation between states of the two open automata that satisfies the conditions of the Definition \ref{Def:OA-Refinement}.
+
 We denote $A_1=  \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}$ and \(A_2 = \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and $A_3 = \OA{S_3}{s_{03}}{J_3}{V_3}{\sigma_{03}}{T_3}$.
@@
 Let us denote with $t^2$ and $t^3$  the elements of $A_2$ and $A_3$ respectively.
-Consider any two states $s_{12} = \mpar{s^1_1,s_2}$ and $s_{13} = \mpar{s^2_1,s_3}$ ($s^1_1$ and $s^2_1$  are the same with renaming).
+Consider any two states $s_{12} = \mpar{s_1,s^1_2}$ and $s_{13} = \mpar{s^2_1,s_3}$ ($s^1_1$ and $s^2_1$  are the same with renaming).
 We define a relation $R'$ relating states of $s_{12}$ and $s_{13}$ as follows:
@@
  v^1_1=v^2_1\wedge s^1_1 = s^2_1\]
-Let us denote $H'=H\uplus J_1 \setminus\{k\}$.
-We want to prove that $\mpar{R', H'}$  is a hole-tracking simulation of $A_{12}$ and $A_{13}$. As for the previous proof we proceed by cases:
+Let us denote $H'=H\cup J_1 \setminus\{k\}$.
+We want to prove that $\mpar{R', H'}$  is a hole-tracking simulation of $A_{12}$ and $A_{13}$. As for the previous proof we deal with cases:
 \begin{enumerate}
@@
 \[\sigma_{012} \uplus \sigma_{013} \vdash R'\mpar{s_{012}, s_{013}}\]
-with $\sigma_{012} = \sigma_{01}^1 \uplus \sigma_{02}$, $\sigma_{013} = \sigma_{01}^2 \uplus \sigma_{03}$, $s_{012}=(s_{01}^1,s_{02})$, and $s_{013}=(s_{01}^2,s_{03})$.
+with $\sigma_{012} = \sigma_{01}^1 \uplus \sigma_{02}$, $\sigma_{013} = \sigma_{01}^2 \uplus \sigma_{03}$, $s_{012}=(s_{01}^1,s_{02})$, and $s_{013}=(s_{01}^2,s_{03})$.\\
 By using the fact that $R$ relates initial configurations of  $A_2$ and $A_3$, we have  the following statement:
-$\mpar{\sigma_{02} \uplus \sigma_{03} \vdash R\mpar{s_{02}, s_{03}}}$,  and based on the  fact that initial states are reachable $\sigma_{012} \vdash \reach{A_{12}}\mpar{s_{012}}$ we have:
+$\mpar{\sigma_{02} \uplus \sigma_{03} \vdash R\mpar{s_{02}, s_{03}}}$,  and relying on the  fact that initial states are reachable $\sigma_{012} \vdash \reach{A_{12}}\mpar{s_{012}}$ we have 
 \[ \mpar{\sigma_{02} \uplus \sigma_{03} \vdash R\mpar{s_{02}, s_{03}}} \wedge 
 \mpar{\sigma_{012} \vdash \reach{A_{12}}\mpar{s_{012}}}\]
-Because initial valuations $\sigma_{01}^1$ and $\sigma_{01}^2$ associate the same values to the ``same'' variables modulo renaming, so the following holds:\\ $\left(\,\,{\displaystyle \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge s^1_1 = s^2_1}\right)\psubst{\sigma_{01}^1 \uplus \sigma_{01}^2 }$.
+Because initial valuations $\sigma_{01}^1$ and $\sigma_{01}^2$ associate the same values to the ``same'' variables modulo renaming, we have the tautology:\\ $\left(\,\,{\displaystyle \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge s^1_1 = s^2_1}\right)\psubst{\sigma_{01}^1 \uplus \sigma_{01}^2 }$.
 
@@
 \end{align*}		
-there exists an indexed family $t_{13x}$ of OTs originating from $s_{13}$ that simulate it: 
+there exists an indexed family $t_{13x}$ of OTs originating from $s_{13}$ that simulates it: 
 \begin{align*}
@@
 \begin{align*}
-&V_{12}= V^1_1\uplus V_2 \text{ and }
+&V_{12}= V^1_1\uplus V_3 \text{ and }
 V_{13}= V^2_1\uplus V_3\\
@@
 \smallskip
-Consider any transition $t_{12}$ in $A_{12}$,  $t_{12}$ is obtained (by case analysis on the definition of composition).
-
-%\begin{enumerate}
-%\item 
-\paragraph{First case: Both automata perform a transition}
-
-$t_{12}$ is obtained  by the composition of transitions $t_2=\OTx{2}{}{2}{2}$ and  \[t_1^1=
+Consider any transition $t_{12}$ in $A_{12}$,  $t_{12}$ is obtained (by case analysis on the definition of composition)
+
+* either by the composition of a transition $t_2=\OTx{2}{}{2}{2}$ and a transition \[t_1^1=
 \OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{   {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1} \qquad \text{ when } k \in {J^1_{1}}^{\prime}
-\]
-The result is the transition:
+\]. We obtain:
+%%%% Attention deactiver ici
 \[
@@
 \[
-t_{13x} = \left(\OT{\mpar{s^2_1, s_3}}{\mpar{{s^2_{1}}',s'_{3x}}}{\alpha^2_{1}}  {{(\beta^2_{1j})^{{j \in J^{2 \prime}_1} \setminus \{k\}}}\uplus \beta_{3xj}^{j \in J'_{3x}  } }{ g^2_1 \wedge  g_{3x}  \wedge \alpha_{3x} =  \beta^2_{1k}}{\psi_{3x} \uplus \psi^2_1}
+t_{13x} = \left(\OT{\mpar{s^2_1, s_3}}{\mpar{{s^2_{1}}',s'_{3x}}}{\alpha^2_{1}}  {{(\beta^2_{1j})^{j \in J^{2 \prime}_1}}\uplus \beta_{3xj}^{j \in J'_{3x}  \setminus \{k\}} }{g_{3x} \wedge g^2_1 \wedge \alpha^2_1 = \beta_{3xk}}{\psi_{3x} \uplus \psi^2_1}
 \right)^{x\in X}\]
 Recall that in this case  $k \in {J^1_{1}}^{\prime}$
-\begin{align*}
-J'_{13} \cap H'  
-&=((J^{2 \prime}_{1} \uplus J'_{3x}) \setminus \mbrc{k}) \cap ((H\uplus J_1) \setminus\{k\} )\\
-& =((J^{2 \prime}_{1} \cap (H\uplus J_1)) \uplus (J'_{3x} \cap  (H\uplus J_1)))\setminus \mbrc{k}\\
-& =((J^{2 \prime}_{1} \cap  J_1)) \uplus (J'_{3x} \cap H))\setminus \mbrc{k}\text{ since }  J^{2 \prime}_{1}\cap H = \emptyset \text{ and } J'_{3x}\cap J_1 = \emptyset  \\
-& =(J^{2 \prime}_{1} \uplus (J'_{3x} \cap H))\setminus \mbrc{k} \text{ since } J^{1 \prime}_{1}\subseteq J_1\\
-& =(J^{1 \prime}_{1} \uplus (J'_{2} \cap H))\setminus \mbrc{k}  \text{ since } J^{1 \prime}_{1}=J^{2 \prime}_{1} \text{ and } J'_2 \cap H = J'_{3x} \cap H\\
-&  =((J^{1 \prime}_{1} \cap J_{1}) \uplus (J'_{2} \cap H))\setminus \mbrc{k} \text{ since } J^{1 \prime}_{1} \subseteq J_1 \\
-& = (J'_{2} \cap (J_1 \uplus H)) \uplus (J^{1 \prime}_{1}\cap (J_1 \uplus H))\setminus \mbrc{k} \text{ since } 
-J_1 \cap  J'_{2}= \emptyset \text{ and } H \cap J^{1 \prime}_{1} = \emptyset\\
-& = ((J'_{2} \uplus J^{1 \prime}_{1})\setminus \mbrc{k}) \cap   ((J_1 \uplus H)\setminus \mbrc{k})\\
-& = J'_{12}\cap H'
-\end{align*}
-In this case the composition gives:
-\[g_{12} \Leftrightarrow g^1_1 \wedge g_2 \wedge \alpha_2=\beta^1_{1k} \text{ and } g_{13x}  \Leftrightarrow g^2_1 \wedge  g_{3x}  \wedge \alpha_{3x}=\beta^2_{1k}\] 
-Furthermore, as $\beta^1_{1k} = \beta^2_{1k}$ then we get:
-\[ g^1_1  \wedge \alpha_2=\beta^1_{1k}  \Leftrightarrow g^2_1  \wedge \alpha_{3x}=\beta^2_{1k}\]
-As the previous case, the rest of the proof is based  on the fact:
-\begin{enumerate}
-\item The composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.
-By construction of  $t_{12}$ and $t_{13}$ we have $\alpha_{12}=
-\alpha^1_{1}$ and $\alpha_{13x}=\alpha^2_{1}$. As  $\alpha^1_{1}=\alpha^2_{1}$  we deduce: 
-$\alpha_{12} = \alpha_{13x}$. 
-\item By composition we have also:\\
- $\beta_{12j}^{j\in J'_{12}}= {({\beta^1_{1j}})^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {\beta_{2j}^{j \in J^{\prime}_2} }}$ and $\beta_{13xj}^{j\in J'_{13}}= {{(\beta^2_{1j})^{j \in {J^{2 \prime}_1} \setminus \{k\}}}\uplus \beta_{3xj}^{j \in J'_{3x} } }$
-
-Therefore, we have for all $j\in J'_{12}$ (recall that $J'_{12}=J'_{13}$):  
-\[\beta_{12j} = \beta_{13xj} \Rightarrow (j\in J^{1 \prime}_1 \land \beta^1_{1j}= \beta^2_{1j}) \vee  (j\in J'_2 \land \beta_{2j} = \beta_{3xj})  \]
-
-\item And considering $\beta^1_{1j}$ and  $\beta^2_{1j}$  are the same (up to renaming)  we have: 
-${\displaystyle V^1_{1} \uplus V^2_{1} \uplus \fvars{t_{1}} \vdash \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1\implies \bigwedge_\subbox{j \in J^{\prime}_1} \beta^1_{1j}= \beta^2_{1j}}$.
-
-Suppose that  $V_{2} \uplus V_{3} \uplus \fvars{t_{3x}}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj}}$ holds then we can deduce:
-\begin{align*}
-V^1_{1} \uplus V^2_{1} \uplus V_{2} \uplus V_{3} \uplus \fvars{t_{13x}}
-\vdash &   \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1\implies \bigwedge_\subbox{j \in J^{\prime}_1} \beta^1_{1j}= \beta^2_{1j} \vee  
-\bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj}\\
-\Rightarrow  V_{12} \uplus V_{13}  \uplus \fvars{t_{13x}}\vdash & 
-\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1
-\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{3x}   \cap H)\uplus J^{1 \prime}_1 } \beta_{12j} = \beta_{13xj}} \\  
-\Rightarrow   V_{12} \uplus V_{13}  \uplus \fvars{t_{13x}} \vdash & 
-\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1
-\implies 
-{\displaystyle \bigwedge_\subbox{j \in ((J'_{3x}   \cap H)\uplus J^{1 \prime}_1)\setminus \{k\} } \beta_{12j} = \beta_{13xj}}\\
-\Rightarrow  V_{12} \uplus V_{13}  \uplus \fvars{t_{13x}} \vdash & 
-\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1
-\implies 
-{\displaystyle \bigwedge_\subbox{j \in (J'_{13x}   \cap H')} \beta_{12j} = \beta_{13xj}}
-\end{align*}
-\end{enumerate}
-From the results (i), (ii), (iii)  and the formula $(*)$ we get:
-\begin{multline*}
-%\everymath{\displaystyle}
-V_2 \uplus V_3 \uplus \fvars{t_2} \vdash\\ R\mpar{s_2, s_3} \wedge g_2 \wedge  \mpar{g^1_1  \wedge \alpha_2=\beta^1_{1k}} \wedge \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1
-\implies\hspace{5em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge\\
-			 g_{3x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
-		\end{array}} \wedge    \mpar{g^2_1  \wedge \alpha_{3x}=\beta^2_{1k}}
-\end{multline*}	
-which can be simplified and re-written as follows:
-\begin{multline*}
-%\everymath{\displaystyle}
-V_{12} \uplus V_{13} \uplus \fvars{t_{13x}} \vdash\\ R\mpar{s_2, s_3} \wedge g_{12} \wedge \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1
-\implies\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge\\
-			 g_{13x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
-		\end{array}} 
-\end{multline*}	
-Furthermore, we have for any transition $t_1$ in $A_1$ relying $s_1$ and $s^{\prime}_1$ and for each $x \in X$ :
-\begin{multline*}
-V_{12} \uplus V_{13}  \uplus \fvars{t_{13x}} \vdash\\
-\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1  \wedge s^1_1 = s^2_1 \implies \bigwedge_\subbox{v_1\in V_1}\!\! \mpar{v^1_1=v^2_1} \psubst{\psi_{13x}} \wedge s^{1\prime}_1 = s^{2\prime}_1 
- \end{multline*}	
-We can deduce for all  $x \in X$ the following statement:
-\begin{multline*}
-V_{12} \uplus V_{13}  \uplus \fvars{t_{13x}} \vdash\\
-\bigwedge_\subbox{v_1\in V_1}\!\!
-v^1_1=v^2_1  \wedge s^1_1 = s^2_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\,\,\everymath{\displaystyle}\bigwedge_\subbox{v_1\in V_1}\!\!
-\mpar{v^1_1=v^2_1} \psubst{\psi_{13x}} \wedge s^{1\prime}_1 = s^{2\prime}_1 }
- \end{multline*}	
-Therefore, we get:
-\begin{multline*}
-%\everymath{\displaystyle}
-V_{12} \uplus V_{13} \uplus \fvars{t_{13x}} \vdash\\ R\mpar{s_2, s_3} \wedge g_{12} \wedge \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1 \wedge s^1_1 = s^2_1
-\implies \hspace{7em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge\\
-			 g_{13x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}} \wedge\bigwedge_\subbox{v_1\in V_1}\!\! \mpar{v^1_1=v^2_1} \psubst{\psi_{13x}} \wedge s^{1\prime}_1 = s^{2\prime}_1
-		\end{array}   } 
-		\end{multline*}
-
-From the hypothesis, we have \(A_1\subst{A_2}{k}\) is non-blocking.  Then, by definition of the reachability  (Definition \ref{Def:Reach}) we have  for all $t_{12} \in T_{12}$:
-\[ \fvars{t_{12}} \vdash \left(\reach{A_{12}}\mpar{s_{12}} \wedge g_{12} \implies \reach{A_{12}}\mpar{s_{12}'}\psubst{\psi_{12}}\right) \]	
-With the conjunction of the  formula obtained above and after simplifying, we get the expected result:
-\begin{multline*}	
-V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \wedge\\[12pt]
-			 g_{13x} \wedge R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
-		\end{array}} 
-	\end{multline*}
-
-\smallskip
-\paragraph{First case: Only the encompassing automaton performs a transition}~\\
-
-$t_{12}$ is obtained  by  the transition $t_1^1=
-\OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{{(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1}$  alone with the state $s_2$ unchanged, if $k \not\in {J^1_{1}}^{\prime}$
-\[t_{12} = \OT{\mpar{s^1_1, s_2}}{\mpar{{s^1_1}', s_2}}{\alpha_1^1}{ {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{g^1_1}{\psi^1_1}
+
+* or by an the transition $t_1^2=
+\OT{ s^2_1}{{s^2_1}'}{\alpha_1^2}{{(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{ g^2_1 }{ \psi^2_1}$  alone with the state $s_2$ unchanged, if $k \not\in {J^1_{1}}^{\prime}$
+\[t_{12} = \OT{\mpar{s^2_1, s_2}}{\mpar{{s^2_1}', s'_2}}{\alpha_1^2}{ {(\beta^2_{1j})^{j \in J^{1 \prime}_1} }}{g^2_1}{\psi^2_1}
 \]
 We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (stated above).
-As  $k \in H$ we have $k \not\in J'_{3x}$ and we build with the same transitions of $A_1$ (up renaming):
-\[t_{13x} = \left(\OT{\mpar{s^2_1, s_3}}{\mpar{{s^2_1}', s_{3}}}{\alpha_1^2}{ {(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{g^2_1}{\psi^2_1} \right)^{x\in X}\]
+As  $k \in H$ we have $k \not\in J'_{2x}$ and we build:
+\[t_{13x} = \left(
+\OT{\mpar{s^1_1, s_3}}{\mpar{s^2_1,s'_{2x}}}{\alpha_{3x}}{\beta_{3xj}^{j \in J'_{3x}}}{g_{3x}}{\psi_{3x}} \right)^{x\in X}\]
+
+~\qed
 \end{enumerate}
-We have to  prove the following formula in both cases (depending on how the transition $t_{12}$ is built): $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$ and
-\begin{multline*}	
-V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \wedge\\[12pt]
-			 g_{13x} \wedge R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
-		\end{array}} 
-	\end{multline*}
-Recall in this case  $k \notin {J^1_{1}}^{\prime}$, so for all $x \in X$ we have:
-\begin{align*}
-	J'_{13x} \cap H' & = J'_{3x}  \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \\
-& = \mpar{J'_{3x}\cap H } \text{ since } J'_{3x}\cap J_1=\emptyset \land k\not\in J'_{3x} \\
-& = \mpar{J'_2\cap H } \text{ since } J'_2 \cap H = J'_{3x} \cap H\\
-& = \mpar{J'_{12}\cap H' } \text{ since } J_2\cap J'_1=\emptyset \land k\not\in {J^1_{1}}^{\prime}
-\end{align*}
-The proof of this case follows the same steps as the previous case the only argument that changes is that by composition we obtain:  $g_{12} \Leftrightarrow g^1_1$ and
-$g_{13x}  \Leftrightarrow g^1_{2}$.
-
-\item It remains to prove the  satisfaction of the  deadlock reducing condition:  for all $\mpar{s_{12}, s_{13}} \in S_{12} \times S_{13}$
-\begin{multline*}
-V_{12} \uplus V_{13} \uplus \biguplus_\subbox{t_{13}\in \fOT{s_{13}}} \fvars{t_{13}} \vdash \\ \left(R^{\prime}\mpar{s_{12}, s_{13}} \wedge \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \implies \bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}} \right)
-\end{multline*}
-
-Let's start with the hypothesis  stating that $\wrel{A_2}{A_3}{H}$, thus we have for all $\mpar{s_{2}, s_3} \in S_2 \times S_3$:
-\begin{multline*}
- V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash \left(R\mpar{s_{2}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_{2p} \in \fOT{s_{2}}} \fguard{t_{2}} \right)
-\end{multline*}
-By adding the same term ${\displaystyle \reach{A_{12}}\mpar{s_{12}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}$ to both sides of the implication, we get:
-\begin{multline*}
- V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash\\ R\mpar{s_{2}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \wedge \reach{A_{12}}\mpar{s_{12}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies\\ \bigvee_\subbox{t_{2p} \in \fOT{s_{2}}} \fguard{t_{2}} \wedge \reach{A_{12}}\mpar{s_{12}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
-\end{multline*}
-that can be re-written
-\begin{multline*}
- V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash\\ R\mpar{s_{2}, s_3} \wedge \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \wedge \reach{A_{12}}\mpar{s_{12}}  \implies \bigvee_\subbox{t_{2} \in \fOT{s_{2}}} \fguard{t_{2}} \wedge \reach{A_{12}}\mpar{s_{12}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
-\end{multline*}
-
-Yet we have by hypothesis  \(A_1\subst{A_2}{k}\) is non-blocking, by definition of non-blocking composition (Definition \ref{Def:Non-blockcomp}) we have:
-\begin{multline*}
- V_{12} \uplus  \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash
- \reach{A_{12}} \mpar{s_{12}}  \wedge  \bigvee_\subbox{t_{1} \in \fOT{s_{1}}} \fguard{t_{1}}  \implies \bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}
-\end{multline*}
-From the two previous formulas and considering that each valuations $\sigma_{1}^1$ and $\sigma_{1}^2$ associate the same values to the ``same'' variables modulo renaming we obtain the expected result.
-
-~\qed
-%\end{enumerate}
 

### 2022-04-15 2021-Refinement/paper/refinementarticle.tex
ajout figues
meeting notes

@@
 
-The next to theorems state that refinement is compositional in the sense that it is sufficient to prove refinement for the composed automata separately to obtain a refinement relation.
+The next two theorems state that refinement is compositional in the sense that it is sufficient to prove refinement for the composed automata separately to obtain a refinement relation.
 This can be split into theorems that can be trivially composed by transitivity.
@@
 
+\begin{center}
+\includegraphics[scale=0.7]{Figures/Theorem2}
+\end{center}
+
 \begin{theorem}[Congruence]\label{thm:Congruence}
@@
 
+\begin{center}
+\includegraphics[scale=0.7]{Figures/Theorem1}
+\end{center}
+
 \TODO{i did not put the global composition theorem, de we state it?}
+
+TODO: FOCUS on the two following items (look at quentin's article):
 

### 2022-04-20 2021-Refinement/paper/refinementarticle.tex
composition is a refinement thm (+lemma tracked holes)

@@
 
+\begin{lemma}[Tracked holes] By construction, if an automaton is the refinement of another one, it is also a refinement by tracking less holes.
+\[\wrel{A_1}{A_2}{H} \land H'\subseteq H \implies \wrel{A_1}{A_2}{H'}\]
+\end{lemma}
 \TODO{example}
@@
 
+\TODO{i did not put the global composition theorem, de we state it?}
+
 \begin{center}
@@
 
-\TODO{i did not put the global composition theorem, de we state it?}
+Open automata compositionis a refinement where
+the tracked holes are the holes of the base automaton minus the composed hole.
+\begin{theorem}[Composition is a refinement]\label{thm:Composition}
+Let $A_1$ and  $A_2$  be three two automata with $J_1$ the set of holes of $A_1$.
+Suppose that \(k \in J_1\) and that \(A_1\subst{A_2}{k}\) is non-blocking. We have:
+\[ \wrel{A_1\subst{A_2}{k}}{A_1}{J_1\setminus \{k\}}\]
+\end{theorem}
 
 TODO: FOCUS on the two following items (look at quentin's article):
-
-- composition is a refinement (under which condition? non-blocking composition?)
 
@@
 
+\section{Proof that Composition is a refinement (Theorem~\ref{thm:Composition})}
+
 \end{document}

### 2022-05-04 2021-Refinement/paper/refinementarticle.tex
add notion of Refusal actions
def refusal traces

@@
 \DeclareMathOperator{\dom}{dom}
+\newcommand{\rightarrowdbl}{\rightarrow\mathrel{\mkern-14mu}\rightarrow}
+
+\newcommand{\xrightarrowdbl}[2][]{%
+  \xrightarrow[#1]{#2}\mathrel{\mkern-14mu}\rightarrow
+}
 
@@
 Unfortunately, this property is not compositional: the composition operator can itself introduce a deadlock.
-In other words, when filling the hole of two related automata with a third one, even if there is a deadlock reduction between the two original automata , there might not be a deadlock reduction in the composed ones.
+In other words, when filling the hole of two related automata with a third one, even if there is a deadlock reduction between the two original automata, there might not be a deadlock reduction in the composed ones.
 The same problem may arise when two related automata are composed in the same hole of a third one.
@@
 
+\TODO{
+A string $t \in \mathcal{A}^*$ is a trace of an automaton if there is some state $s$ such that $s_0 \xrightarrowdbl{t}  s$. We denote the set of traces of an automaton $A$ by $\mathcal{T}_A$. \\
+Notion of Extension refinement. May be we need to introduce the notion of  refusal of
+a trace $t \in \mathcal{T}_A$ is a set of actions such that all actions in the set can be refused after the automaton $A$
+has executed the trace $t$.
+\[X \in \bot_{A}(t) \Leftrightarrow \{\exists s.
+s_0  \xrightarrowdbl{t} s \wedge \forall a \in X.
+s \not{\xrightarrow{a}}    \}\] and replace deadlock reducing, under (3) by
+\[\forall t \in \mathcal{T}_{A_1} \cap  \mathcal{T}_{A_2},\, \bot_{A_2}(t) \subseteq  \bot_{A_1}(t)  \] } 
 \begin{lemma}[Tracked holes] By construction, if an automaton is the refinement of another one, it is also a refinement by tracking less holes.

### 2022-05-13 2021-Refinement/paper/refinementarticle.tex
definition to discuss
meeting note

@@
 
+\begin{definition}[XXX]\label{def:???} \TODO{To check}\\
+Let \(\OAg[1]\) and \(\OAg[2]\) be two OAs.
+A relation \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) on OA   is XXXX if  it satisfies the following:
+\begin{multline*}
+\forall \mpar{s_1, s_2} \in S_1 \times S_2,  V_1 \uplus V_2\vdash \\ \bigsymb{\exists} \mpar{t_1, t_2} \defobject \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \wedge R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j}\\ \implies  R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}\\
+\end{multline*}
+\end{definition}
+
 \begin{definition}[Deadlock reduction]\label{def:dpwd}\\
@@
 \[\forall t \in \mathcal{T}_{A_1} \cap  \mathcal{T}_{A_2},\, \bot_{A_2}(t) \subseteq  \bot_{A_1}(t)  \] }
+
+\TODO{thm: our new definition is equivalent to extension refinement in case there is no hole and no guard}
+
 \begin{lemma}[Tracked holes] By construction, if an automaton is the refinement of another one, it is also a refinement by tracking less holes.

### 2022-05-17 2021-Refinement/paper/refinementarticle.tex
refine comparison extension
proof transitivity revisite

--- 2022-05-04 2021-Refinement/paper/refinementarticle.tex
@@
 
+\begin{definition}[XXX]\label{def:???} \TODO{To check}\\
+Let \(\OAg[1]\) and \(\OAg[2]\) be two OAs.
+A relation \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) on OA   is XXXX if  it satisfies the following:
+\begin{multline*}
+\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_2} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\  V_1 \uplus V_2 \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \implies  R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}\\
+\end{multline*}
+\end{definition}
+
 \begin{definition}[Deadlock reduction]\label{def:dpwd}\\
@@
 \begin{multline*}
- \forall \mpar{s_1, s_2} \in S_1 \times S_2,\\ V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
+ \forall \mpar{s_1, s_2} \in S_1 \times S_2,
+ \\ V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
 \end{multline*}
@@
 \end{multline*}
-\item[(3)] $R$ is deadlock reducing.
+\item[(3)] $R$ satisfies XXXXX.
 
@@
 \medskip
-\item Finally, we need to prove the satisfaction of the  deadlock reducing condition.
-According to the refinement relation relating   $A_2$ and $A_3$ we have for all $\mpar{s_{2p}, s_3} \in S_2 \times S_3$:
-\begin{multline*}
- V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash \left(R_{23}\mpar{s_{2p}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} \right)
-\end{multline*}
-By adding the term $R_{12}\mpar{s_1,s_{2p}}$ to both sides of the implication, we get:
-\begin{multline*}
-V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_{2p}} \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash \\
-R_{12}\mpar{s_1,s_{2p}}\wedge R_{23}\mpar{s_{2p}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies R_{12}\mpar{s_1,s_{2p}}\wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}}
-\end{multline*}
-This is valid for all $s_{2p} \in (s_{2p})^{p\in P}$ then we have:
-\begin{multline*}
-V_1 \uplus V_2 \uplus V_3 \uplus \biguplus_\subbox{p \in P} \fvars{t_{2p}} \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash \\
-\operatorname*{\bigsymb{\bigvee}}_{p\in P}\mpar{
-R_{12}\mpar{s_1,s_{2p}}\wedge R_{23}\mpar{s_{2p}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies R_{12}\mpar{s_1,s_{2p}}\wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}}}
-\end{multline*}
-This results in:
-\begin{multline*}
-V_1 \uplus V_2 \uplus V_3 \uplus\biguplus_\subbox{p \in P} \fvars{t_{2p}} \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash \\
-R_{13}\mpar{s_1,s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \operatorname*{\bigsymb{\bigvee}}_{p\in P}\mpar{ R_{12}\mpar{s_1,s_{2p}}\wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}}}
-\end{multline*}
-Yet according to the relation between $A_1$ and $A_2$ we have  for all $\mpar{s_1, s_{2p}} \in S_1 \times S_2$:
-\begin{multline*}
- V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{2p} \in \fOT{s_{2p}}} \fvars{t_{2p}} \vdash R_{12}\mpar{s_1, s_{2p}} \wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
-\end{multline*}
-
-This formula is valid for all $s_{2p} \in (s_{2p})^{p\in P}$,  thus we can state the following:
-\begin{multline*}
- V_1 \uplus V_2 \uplus \biguplus_{\mathclap{\substack{t_{2p} \in \fOT{s_{2p}}\\ p \in P}}} \fvars{t_{2p}} 
-\vdash \\
-\operatorname*{\bigsymb{\bigvee}}_{p\in P}\mpar{R_{12}\mpar{s_1, s_{2p}} \wedge \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}} }  \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
-\end{multline*}
-By using transitive property of implication on formula obtained form both relations and by removing the $A_2$ variables that have not effect on   $A_1$ et  $A_3$, we get the desired result:
-\begin{multline*}
-V_1 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3}
-\vdash R_{13}\mpar{s_1,s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3}
-\implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
+\item Finally, we need to prove the satisfaction of ??? \TODO{to check}.
+
+According to the refinement relation between  $A_1$ and $A_2$ we have for all $\mpar{s_1,s_{2}} \in S_1 \times S_2$:
+\begin{multline*}
+\bigsymb{\forall} \mpar{t_1, t_{2}} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\  V_1 \uplus V_2 \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R_{12}\mpar{s_1, s_2} \wedge 	g_1 \wedge g_{2} \wedge \alpha_1 = \alpha_{2} \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2}} \beta_{1j} = \beta_{2j} \implies  R_{12}\mpar{s'_1, s'_{2}}\psubst{\psi_1 \uplus \psi_2}
+\end{multline*}
+
+Yet according to the relation between   $A_2$ and $A_3$ we have for all $\mpar{s_2,s_3} \in S_2 \times S_3$:
+\begin{multline*}
+\bigsymb{\forall} \mpar{t_2, t_{3}} = \mpar{\OTx{2}{}{2}{2}, \OTx{3}{}{3}{3}} \in \fOT{s_2} \times \fOT{s_3} \\  V_2 \uplus V_3 \uplus \fvars{t_2} \uplus \fvars{t_3} \vdash \hspace{6cm}\\  R_{23}\mpar{s_2, s_3} \wedge 	g_2 \wedge g_{3} \wedge \alpha_2 = \alpha_{3} \wedge \bigwedge_\subbox{j \in J'_2 \cap J'_{3}} \beta_{2j} = \beta_{3j} \implies  R_{23}\mpar{s'_2, s'_{3}}\psubst{\psi_2 \uplus \psi_3}
+\end{multline*}
+
+We can make the conjunction of these two formulas,  for each $s_2 \in S_2$  relating $s_1$ and $s_3$.
+Thus, we get  $\forall \mpar{s_1,s_2,s_3} \in S_1\times S_2 \times S_3$ and $\bigsymb{\forall} \mpar{t_1,t_2, t_{3}}\!=\!
+\mpar{\OTx{1}{}{1}{1},\OTx{2}{}{2}{2},\OTx{3}{}{3}{3}}\!
+\in\!
+\fOT{s_1} \times\fOT{s_2} \times \fOT{s_3}$
+\begin{multline*}
+V_1\uplus V_2 \uplus V_3 \uplus \fvars{t_1} \uplus \fvars{t_2} \uplus \fvars{t_3} \vdash \left(R_{12}\mpar{s_1, s_2} \wedge   g_1 \wedge g_{2} \wedge \alpha_1 = \alpha_{2} \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2}} \beta_{1j} = \beta_{2j}\right) \wedge\\ \mpar{R_{23}\mpar{s_2, s_3}
+\wedge  g_2 \wedge g_{3} \wedge \alpha_2 = \alpha_{3} \wedge \bigwedge_\subbox{j \in J'_2 \cap J'_{3}} \beta_{2j} = \beta_{3j}} \implies R_{12}\mpar{s'_1, s'_{2}}\psubst{\psi_1 \uplus \psi_2} \wedge R_{23}\mpar{s'_2, s'_{3}}\psubst{\psi_2 \uplus \psi_3}
+\end{multline*}
+By rearranging and simplifying we get:$\forall \mpar{s_1,s_2,s_3} \in S_1\times S_2 \times S_3$, $ \bigsymb{\forall} \mpar{t_1,t_2, t_{3}}\!=\!
+\\\mpar{\OTx{1}{}{1}{1},\OTx{2}{}{2}{2},\OTx{3}{}{3}{3}}\!
+\in\!
+\fOT{s_1} \times\fOT{s_2} \times \fOT{s_3}$\\
+\begin{multline*}
+V_1\uplus V_2 \uplus V_3 \uplus \fvars{t_1} \uplus \fvars{t_2} \uplus \fvars{t_3} \vdash \underbrace{R_{12}\mpar{s_1, s_2} \wedge  R_{23}\mpar{s_2, s_3}}_{R_{13}\mpar{s_1, s_3}} \wedge \\ g_1  \wedge g_{3}
+\wedge \alpha_1 = \alpha_{3}  \wedge \bigwedge_\subbox{j \in J'_1\cap J'_2 \cap J'_{3}} \beta_{1j} = \beta_{3j}
+ \implies \underbrace{R_{12}\mpar{s'_1, s'_{2}}\wedge R_{23}\mpar{s'_2, s'_{3}}}_{R_{13}\mpar{s'_1, s'_3}} \psubst{\psi_1 \uplus \psi_2\uplus \psi_3 } 
+\end{multline*}
+By removing the $A_2$ variables that have not effect on   $A_1$ et  $A_3$, we get the desired result: $\forall \mpar{s_1,s_3} \in S_1 \times S_3$, $\bigsymb{\forall} \mpar{t_1,t_2, t_{3}}\!=\!
+\mpar{\OTx{1}{}{1}{1},\OTx{3}{}{3}{3}}\!
+\in\!
+\fOT{s_1} \times \fOT{s_3}$
+\begin{multline*}
+V_1 \uplus V_3 \uplus \fvars{t_1}  \uplus \fvars{t_3} \vdash R_{13}\mpar{s_1, s_3} \wedge \\ g_1 \wedge g_{2} \wedge g_{3}
+\wedge \alpha_1 = \alpha_{3}  \wedge \bigwedge_\subbox{j \in J'_1\cap  J'_{3}} \beta_{1j} = \beta_{3j}
+ \implies R_{13}\mpar{s'_1, s'_3} \psubst{\psi_1 \uplus \psi_3 } 
 \end{multline*}

### 2022-05-18 2021-Refinement/paper/refinementarticle.tex
thm 1

@@
 \[\forall t \in \mathcal{T}_{A_1} \cap  \mathcal{T}_{A_2},\, \bot_{A_2}(t) \subseteq  \bot_{A_1}(t)  \] }
+
+\TODO{thm: backward compatibility + simulation is equivalent to extension refinement in case there is no hole and no guard, i.e. in case the definitions of automata coincide}
+
 \begin{lemma}[Tracked holes] By construction, if an automaton is the refinement of another one, it is also a refinement by tracking less holes.
@@
 \medskip
-\item Finally, we need to prove the satisfaction of ??? \TODO{to check}.
-
-According to the refinement relation between  $A_1$ and $A_2$ we have for all $\mpar{s_1,s_{2}} \in S_1 \times S_2$:
+\item  \TODO{Part to check} Finally, we have to prove the following holds:
+$\forall \mpar{s_1,s_3} \in S_1 \times S_3$, $\bigsymb{\forall} \mpar{t_1,t_2, t_{3}}\!=\! \mpar{\OTx{1}{}{1}{1},\OTx{3}{}{3}{3}}\! \in\! \fOT{s_1} \times \fOT{s_3}$
+\begin{multline*}
+V_1 \uplus V_3 \uplus \fvars{t_1}  \uplus \fvars{t_3} \vdash R_{13}\mpar{s_1, s_3} \wedge \\ g_1 \wedge g_{2} \wedge g_{3}
+\wedge \alpha_1 = \alpha_{3}  \wedge \bigwedge_\subbox{j \in J'_1\cap  J'_{3}} \beta_{1j} = \beta_{3j}
+ \implies R_{13}\mpar{s'_1, s'_3} \psubst{\psi_1 \uplus \psi_3 } 
+\end{multline*}
+
+As well,  according to the refinement relation between  $A_1$ and $A_2$ that for all $\mpar{s_1,s_{2}} \in S_1 \times S_2$:
 \begin{multline*}
@@
 \end{multline*}
-By removing the $A_2$ variables that have not effect on   $A_1$ et  $A_3$, we get the desired result: $\forall \mpar{s_1,s_3} \in S_1 \times S_3$, $\bigsymb{\forall} \mpar{t_1,t_2, t_{3}}\!=\!
-\mpar{\OTx{1}{}{1}{1},\OTx{3}{}{3}{3}}\!
-\in\!
-\fOT{s_1} \times \fOT{s_3}$
-\begin{multline*}
-V_1 \uplus V_3 \uplus \fvars{t_1}  \uplus \fvars{t_3} \vdash R_{13}\mpar{s_1, s_3} \wedge \\ g_1 \wedge g_{2} \wedge g_{3}
-\wedge \alpha_1 = \alpha_{3}  \wedge \bigwedge_\subbox{j \in J'_1\cap  J'_{3}} \beta_{1j} = \beta_{3j}
- \implies R_{13}\mpar{s'_1, s'_3} \psubst{\psi_1 \uplus \psi_3 } 
-\end{multline*}
+By removing the $A_2$ variables that have not effect on   $A_1$ et  $A_3$, we get the desired result.
 

### 2022-05-19 2021-Refinement/paper/refinementarticle.tex
Proof

@@
 
-As well,  according to the refinement relation between  $A_1$ and $A_2$ that for all $\mpar{s_1,s_{2}} \in S_1 \times S_2$:
+According to the refinement relation between  $A_1$ and $A_2$ we have, for all $\mpar{s_1,s_{2}} \in S_1 \times S_2$:
 \begin{multline*}
@@
 
-We can make the conjunction of these two formulas,  for each $s_2 \in S_2$  relating $s_1$ and $s_3$.
+We can make the conjunction of these two formulas.
+For each $s_2 \in S_2$, we remark that  $s_2$  allows to relate $s_1$ and $s_3$ if and only if $R_{12}\mpar{s_1, s_2}\land \mpar{R_{23}\mpar{s_2, s_3}} $.
 Thus, we get  $\forall \mpar{s_1,s_2,s_3} \in S_1\times S_2 \times S_3$ and $\bigsymb{\forall} \mpar{t_1,t_2, t_{3}}\!=\!
@@
 \end{multline*}
+Note that if  $R_{12}\mpar{s_1, s_2}$ or $ \mpar{R_{23}\mpar{s_2, s_3}}$ is false the statement trivially holds.
+
 By rearranging and simplifying we get:$\forall \mpar{s_1,s_2,s_3} \in S_1\times S_2 \times S_3$, $ \bigsymb{\forall} \mpar{t_1,t_2, t_{3}}\!=\!
@@
 \end{multline*}
-By removing the $A_2$ variables that have not effect on   $A_1$ et  $A_3$, we get the desired result.
+By removing the variables of $A_2$ that have not effect on   $A_1$ et  $A_3$, we get the desired result.
 

### 2022-05-19 2021-Refinement/paper/refinementarticle.tex
preservation along simultaneous transitions

@@
 
-\begin{definition}[XXX]\label{def:???} \TODO{To check}\\
+\begin{definition}[Preservation along simultaneous transitions]\label{def:preservation} \\
 Let \(\OAg[1]\) and \(\OAg[2]\) be two OAs.
-A relation \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) on OA   is XXXX if  it satisfies the following:
+A relation \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) between  \(\OAg[1]\) and \(\OAg[2]\)
+  is preserved along simultaneous transitions if  it satisfies the following:
 \begin{multline*}

### 2022-05-19 2021-Refinement/paper/refinementarticle.tex
def 10 et 11
commented wrong def

@@
 
-\begin{definition}[Deadlock reduction]\label{def:dpwd}\\
-Let \(\OAg[1]\) and \(\OAg[2]\) be two OAs.
-A relation on OA configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if  it satisfies the following\footnote{Note that variables of $T_1$ are existentially quantified in the proposition.}:
-\begin{multline*}
- \forall \mpar{s_1, s_2} \in S_1 \times S_2,
- \\ V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
-\end{multline*}
-\end{definition}
+%
+%\begin{definition}[Deadlock reduction]\label{def:dpwd}\\
+%Let \(\OAg[1]\) and \(\OAg[2]\) be two OAs.
+%A relation on OA configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if  it satisfies the following\footnote{Note that variables of $T_1$ are existentially quantified in the proposition.}:
+%\begin{multline*}
+% \forall \mpar{s_1, s_2} \in S_1 \times S_2,
+% \\ V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
+%\end{multline*}
+%\end{definition}
 
@@
 \end{multline*}
-\item[(3)] $R$ is deadlock reducing.
+\item[(3)] $R$ is  is preserved along simultaneous transitions of \(A_1\) and \(A_2\).
 \end{definition}
@@
 \end{multline*}
-\item[(3)] $R$ satisfies XXXXX.
+\item[(3)] $R$ is preserved along simultaneous transitions of \(A_1\) and \(A_2\).
 

### 2022-05-31 2021-Refinement/paper/refinementarticle.tex
proof continue...

@@
 
-\end{enumerate}
-
 These two cases define (depending on how $t_{13}$ is built) the family $t_{23x}$ of OTs we are looking for.
@@
 The proof of the rest of the formula follows the same steps as the previous case the only argument that changes is that by composition we obtain:  $g_{13} \Leftrightarrow g_1$ and
-$g_{23x}  \Leftrightarrow g_{2x}$.
-
-\item The last formula we need to prove is the following: for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
+$g_{23x}  \Leftrightarrow g_{2x}$.\\
+
+\TODO{XXXXXXXXXXXXXXXXX}
+\item The last formula we need to prove is that the relation is preserved along simultaneous transitions, i.e. for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$ and
+\begin{multline*}
+ \bigsymb{\forall} \mpar{t_{13}, t_{23}} = \mpar{\OTx{13}{}{13}{13}, \OTx{23}{}{23}{23}} \in \fOT{s_{13}} \times \fOT{s_{23}} \\  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} \vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} \wedge \bigwedge_\subbox{j \in J'_{13} \cap J'_{23}} \beta_{13j} = \beta_{23j} \implies  R'\mpar{s'_{13}, s'_{23}}\psubst{\psi_{13} \uplus \psi_{23}}\\
+\end{multline*}
+
+According to the refinement relation between  $A_1$ and $A_2$ we have, for all $\mpar{s_1,s_{2}} \in S_1 \times S_2$ and
+\begin{multline*}
+\bigsymb{\forall} \mpar{t_1, t_{2}} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\  V_1 \uplus V_2 \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_{2} \wedge \alpha_1 = \alpha_{2} \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2}} \beta_{1j} = \beta_{2j} \implies  R\mpar{s'_1, s'_{2}}\psubst{\psi_1 \uplus \psi_2}
+\end{multline*}
+
+The reachability of a state ensures that $\bigsymb{\forall} t_{13} = \OTx{13}{}{13}{13} \in T_{13}$
+\[\fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi}\right)\]
+
+~~\\
+~~\\
+
+The last formula we need to prove is the following: for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
 \begin{multline*}
@@
 
+\end{enumerate}
 \section{Proof of Congruence (Theorem~\ref{thm:Congruence})}

### 2022-06-02 2021-Refinement/paper/refinementarticle.tex
small changes
proof thm to discuss

@@
 		\bigsymb{\forall} t_1 = \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\[10pt]
-		\quad \mpar{\forall x \in X, J'_{2x}= J'_1} \\[2pt]
-		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\
+		\quad \mpar{\forall x \in X, J'_{2x}= J'_1} \nwedge\\[2pt]
+		 V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\
 \hspace{5em} \left( R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x}} \beta_{1j} = \beta_{2xj} \\[12pt]
-			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x}} \beta_{1j} = \beta_{2xj} \nwedge\\[12pt]
+			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
 		\end{array}}\right)
@@
 		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\[12pt]
-		\quad \mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H} \\[1pt]
-		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\\hspace{5em} \mpar{R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \\
-			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\quad \mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H} \nwedge\\[1pt]
+		 V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\\hspace{5em} \mpar{R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}   \nwedge\\
+			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
 		\end{array}}} 
@@
 \medskip
-\item  \TODO{Part to check} Finally, we have to prove the following holds:
+\item  Finally, we have to prove the following holds:
 $\forall \mpar{s_1,s_3} \in S_1 \times S_3$, $\bigsymb{\forall} \mpar{t_1,t_2, t_{3}}\!=\! \mpar{\OTx{1}{}{1}{1},\OTx{3}{}{3}{3}}\! \in\! \fOT{s_1} \times \fOT{s_3}$
@@
 
-Yet according to the relation between   $A_2$ and $A_3$ we have for all $\mpar{s_2,s_3} \in S_2 \times S_3$:
+Yet according to the relation between   $A_2$ and $A_3$ we have  $\forall \mpar{s_2,s_3} \in S_2 \times S_3$ and
 \begin{multline*}
@@
 We can make the conjunction of these two formulas.
-For each $s_2 \in S_2$, we remark that  $s_2$  allows to relate $s_1$ and $s_3$ if and only if $R_{12}\mpar{s_1, s_2}\land \mpar{R_{23}\mpar{s_2, s_3}} $.
+For each $s_2 \in S_2$, we remark that  $s_2$  allows to relate $s_1$ and $s_3$ if and only if $R_{12}\mpar{s_1, s_2}\land R_{23}\mpar{s_2, s_3} $.
 Thus, we get  $\forall \mpar{s_1,s_2,s_3} \in S_1\times S_2 \times S_3$ and $\bigsymb{\forall} \mpar{t_1,t_2, t_{3}}\!=\!
@@
 \begin{multline*}
-V_1\uplus V_2 \uplus V_3 \uplus \fvars{t_1} \uplus \fvars{t_2} \uplus \fvars{t_3} \vdash \left(R_{12}\mpar{s_1, s_2} \wedge   g_1 \wedge g_{2} \wedge \alpha_1 = \alpha_{2} \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2}} \beta_{1j} = \beta_{2j}\right) \wedge\\ \mpar{R_{23}\mpar{s_2, s_3}
-\wedge  g_2 \wedge g_{3} \wedge \alpha_2 = \alpha_{3} \wedge \bigwedge_\subbox{j \in J'_2 \cap J'_{3}} \beta_{2j} = \beta_{3j}} \implies R_{12}\mpar{s'_1, s'_{2}}\psubst{\psi_1 \uplus \psi_2} \wedge R_{23}\mpar{s'_2, s'_{3}}\psubst{\psi_2 \uplus \psi_3}
+V_1\uplus V_2 \uplus V_3 \uplus \fvars{t_1} \uplus \fvars{t_2} \uplus \fvars{t_3} \vdash\\ \left(R_{12}\mpar{s_1, s_2} \wedge   g_1 \wedge g_{2} \wedge \alpha_1 = \alpha_{2} \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2}} \beta_{1j} = \beta_{2j}\right) \wedge \hspace{2.5cm}\\ \mpar{R_{23}\mpar{s_2, s_3}
+\wedge  g_2 \wedge g_{3} \wedge \alpha_2 = \alpha_{3} \wedge \bigwedge_\subbox{j \in J'_2 \cap J'_{3}} \beta_{2j} = \beta_{3j}} \implies\\ R_{12}\mpar{s'_1, s'_{2}}\psubst{\psi_1 \uplus \psi_2} \wedge R_{23}\mpar{s'_2, s'_{3}}\psubst{\psi_2 \uplus \psi_3}
 \end{multline*}
@@
 
-\TODO{XXXXXXXXXXXXXXXXX}
-\item The last formula we need to prove is that the relation is preserved along simultaneous transitions, i.e. for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$ and
+\TODO{To discuss the following:} 
+\item The last formula we need to prove is that the relation is preserved along simultaneous transitions, i.e. the following is satisfied  $\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$ and
 \begin{multline*}
@@
 
-According to the refinement relation between  $A_1$ and $A_2$ we have, for all $\mpar{s_1,s_{2}} \in S_1 \times S_2$ and
+Let's start  with the hypothesis of the theorem stating that $\wrel{A_1}{A_2}{H}$, thus we have   $\forall \mpar{s_1,s_{2}} \in S_1 \times S_2$ and
 \begin{multline*}
@@
 
-The reachability of a state ensures that $\bigsymb{\forall} t_{13} = \OTx{13}{}{13}{13} \in T_{13}$
-\[\fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi}\right)\]
-
+We have a second hypothesis stating that the result of the composition \(A_1\subst{A_3}{k}\) is non-blocking, by Definition \ref{Def:Non-blockcomp} we have:
+\begin{multline*}
+V_{13}  \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \left( \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \right)
+\end{multline*}
+
+Based on the definition of reachability of a state (Definition \ref{Def:Reach}) we have $\bigsymb{\forall} t_{13} = \OTx{13}{}{13}{13} \in T_{13}$
+\[\fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right)\]
+\begin{multline*}
+\vdash\\ \underbrace{R\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3}_{R^{\prime}(s_{13},s_{23})}  \wedge \dots \implies \ldots 
+\end{multline*}
 ~~\\
 ~~\\
-
+\TODO{Until here}
 The last formula we need to prove is the following: for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$

### 2022-06-02 2021-Refinement/paper/refinementarticle.tex
terminology

--- 2022-05-31 2021-Refinement/paper/refinementarticle.tex
@@
 
-\begin{definition}[Preservation along simultaneous transitions]\label{def:preservation} \\
+\begin{definition}[Preservation along identical transitions]\label{def:preservation} \\
 Let \(\OAg[1]\) and \(\OAg[2]\) be two OAs.
 A relation \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) between  \(\OAg[1]\) and \(\OAg[2]\)
-  is preserved along simultaneous transitions if  it satisfies the following:
+  is preserved along identical transitions if  it satisfies the following:
 \begin{multline*}
@@
 \end{multline*}
-\item[(3)] $R$ is  is preserved along simultaneous transitions of \(A_1\) and \(A_2\).
+\item[(3)] $R$ is  is preserved along identical transitions of \(A_1\) and \(A_2\).
 \end{definition}
@@
 \end{multline*}
-\item[(3)] $R$ is preserved along simultaneous transitions of \(A_1\) and \(A_2\).
+\item[(3)] $R$ is preserved along identical transitions of \(A_1\) and \(A_2\).
 
@@
 \TODO{XXXXXXXXXXXXXXXXX}
-\item The last formula we need to prove is that the relation is preserved along simultaneous transitions, i.e. for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$ and
+\item The last formula we need to prove is that the relation is preserved along identical transitions, i.e. the following is satisfied  $\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$ and
 \begin{multline*}
@@
 
-According to the refinement relation between  $A_1$ and $A_2$ we have, for all $\mpar{s_1,s_{2}} \in S_1 \times S_2$ and
+According to the refinement relation between  $A_1$ and $A_2$ we have,  $\forall \mpar{s_1,s_{2}} \in S_1 \times S_2$ and
 \begin{multline*}

### 2022-06-02 2021-Refinement/paper/refinementarticle.tex

--- 2022-06-02 2021-Refinement/paper/refinementarticle.tex
@@
 \TODO{To discuss the following:} 
-\item The last formula we need to prove is that the relation is preserved along simultaneous transitions, i.e. the following is satisfied  $\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$ and
+\item The last formula we need to prove is that the relation is preserved along identical transitions, i.e. the following is satisfied  $\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$ and
 \begin{multline*}

### 2022-06-03 2021-Refinement/paper/refinementarticle.tex
work session
beter holes in identical transition condition

@@
 
+\begin{definition}[Preservation along identical transitions]\label{def:preservation} \\
+Let \(\OAg[1]\) and \(\OAg[2]\) be two OAs.
+A relation \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) between  \(\OAg[1]\) and \(\OAg[2]\)
+  is preserved along identical transitions if  it satisfies the following:
+\begin{multline*}
+\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_2} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\  V_1 \uplus V_2 \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2
+%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} 
+\implies \\
+\exists
+\OTx{1}{a}{3}{3}\in \fOT{s_1}. \alpha_1=\alpha_{1 a} \land g_{1 a} \land \bigwedge_\subbox{j \in J'_3 \cap J'_2} \beta_{2j} = \beta_{3j}\land
+ R\mpar{s'_{1 a}, s'_2}\psubst{\psi_{1 a} \uplus \psi_2}\\
+\end{multline*}
+\end{definition}
+\TODO{check les actions des trous -- Je pense que c est mieux maintenant}
 %
@@
 The same problem may arise when two related automata are composed in the same hole of a third one.
+
+\TODO{add a notion of composable at hole i:
+An OA is composable at hole k if it is partially deterministic relatively to actions of hole k
+}
+
+\begin{multline*}
+\forall s_1\in S,\, \forall \OTx{1}{a}{1}{1}, \OTx{1}{b}{2}{2} \in \fOT{s_1}.\\
+\neg\left(\alpha_{1 a} = \alpha_{1 b}\land s'_{1 a}\neq s'_{1 b}\land g_{1 a}\land g_{1 b} \land\beta_{1 k} \neq \beta_{2 k}\right)
+\end{multline*}
+
+An composable automaton cannot transform external non-determinism of the sub-automaton into internal non-determinism.
 

### 2022-06-08 2021-Refinement/paper/refinementarticle.tex
proof sketch composition

@@
 
-\TODO{To discuss the following:} 
-\item The last formula we need to prove is that the relation is preserved along identical transitions, i.e. the following is satisfied  $\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$ and
+\item The last formula we need to prove is that the relation is preserved along identical transitions, i.e. the following is satisfied 
+\TODO{NEW PROOF SKETCH}
+HYPOTHESES and OBJECTIVES
+
+TWO cases for the OT $t_{23}$
+
+CASE 1 : $k$ does not move in $A_2$
+
+two cases for  $t_{13}$
+
+ ...
+
+in both cases relation is preserved along identical transitions applied on A1 vs A2 provides a $t_{1}'$ such that HOLE $k$ does not move
+
+and has the desired property for ``relation is preserved along identical transitions''
+
+CASE 2 : k moves in $A_2$ with action $\beta_{2 k}$, and $A_3$ does the labelled action $\beta_{2 k}$.
+
+two cases for  $t_{13}$
+
+ ...
+
+in both cases relation is preserved along identical transitions applied on A1 vs A2 provides a $t_{1}'$ such that HOLE $k$ should move with the action $\beta_{2 k}$.
+
+We recompose a $t_{1}'$ with $t_{1}'$ and $t_3$ from  $t_{23}$
+
+it has the desired property for ``relation is preserved along identical transitions''
+
+relation on guards should hold but to be formulated carefully.
+
+\TODO{END OF NEW PROOF SKETCH}
+ $\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$ and
 \begin{multline*}

### 2022-06-08 2021-Refinement/paper/refinementarticle.tex
work at GDR: new definition 7

@@
 \end{figure}
-
-\section{A First Refinement Relation}\label{sec:refinement}
+\subsection{Reachability : check if useful?}
+\begin{definition}[Reachability] \label{Def:Reach}
+For any open automata \(A = \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is any predicate on states that is valid on initial state, and preserved across transitions:
+\[\sigma_0 \vdash \reach{A}\mpar{s_0}\quad\land\quad\forall t = \OTg \in T, \fvars{t} \vdash \left(\reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}\right)\]
+\end{definition}
+Reachability takes into account all paths, and can over-approximate the reachable configurations. 
+From an automation point of view, finding the most precise reachability predicate for a given automata is not decidable because of the symbolic nature of open automata, but only an over-approximation is necessary.
+An automatic tool would only need to find an over approximation of reachability to reason on composition that is compatible with deadlock reduction.
+We call \emph{non-blocking composition} a composition that can be safely be used to compose open automata that are involved in a deadlock reducing relation.
+
+\section{Refinement Relations for automata with the same holes}\label{sec:refinement}
 
@@
 
-\TODO{check deadlock reduction/reducing in the literature}
-We first define when a relation is deadlock reducing, before characterising a first simple refinement relation  to compare automata with identical holes.
-
-\subsection{Deadlock Reduction, Reachability, and Composition}
-
-A notion that is often used in the context of refinement is the notion of deadlock reduction.
-This property considers that two states related by a given relation and states that if one state can do a transition, then the other can do a transition too.
-This notion is not much interesting in the general case as there is a priori no relation between the two transitions.
-However, when the relation that relates states is a simulation, this will relate the possible transitions and the deadlock reduction will become a valuable property.
-
-Next definition states that if $T_2$ is not in a deadlock position then $T_1$ can do a transition but not necessarily with the same input values.
-This is very weak but sufficient when composed with the def  of simulation.
-
-\begin{definition}[Preservation along identical transitions]\label{def:preservation} \\
-Let \(\OAg[1]\) and \(\OAg[2]\) be two OAs.
-A relation \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) between  \(\OAg[1]\) and \(\OAg[2]\)
-  is preserved along identical transitions if  it satisfies the following:
-\begin{multline*}
-\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_2} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\  V_1 \uplus V_2 \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \implies  R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}\\
-\end{multline*}
-\end{definition}
-
-\begin{definition}[Preservation along identical transitions]\label{def:preservation} \\
-Let \(\OAg[1]\) and \(\OAg[2]\) be two OAs.
-A relation \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) between  \(\OAg[1]\) and \(\OAg[2]\)
-  is preserved along identical transitions if  it satisfies the following:
-\begin{multline*}
-\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_2} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\  V_1 \uplus V_2 \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2
-%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} 
-\implies \\
-\exists
-\OTx{1}{a}{3}{3}\in \fOT{s_1}. \alpha_1=\alpha_{1 a} \land g_{1 a} \land \bigwedge_\subbox{j \in J'_3 \cap J'_2} \beta_{2j} = \beta_{3j}\land
- R\mpar{s'_{1 a}, s'_2}\psubst{\psi_{1 a} \uplus \psi_2}\\
-\end{multline*}
-\end{definition}
-\TODO{check les actions des trous -- Je pense que c est mieux maintenant}
+%\TODO{check deadlock reduction/reducing in the literature}
+
 %
@@
 
-Because of the symbolic nature of OAs and their structure, in this definition,  the fact that a guard is true is sufficient to reason on the possible paths.
+%Because of the symbolic nature of OAs and their structure, in this definition,  the fact that a guard is true is sufficient to reason on the possible paths.
 This slightly simplifies the definition and makes the characterisation of transition that can be triggered very symbolic.
@@
 
-Unfortunately, this property is not compositional: the composition operator can itself introduce a deadlock.
+%Unfortunately, this property is not compositional: the composition operator can itself introduce a deadlock.
 In other words, when filling the hole of two related automata with a third one, even if there is a deadlock reduction between the two original automata, there might not be a deadlock reduction in the composed ones.
@@
 
-\TODO{add a notion of composable at hole i:
-An OA is composable at hole k if it is partially deterministic relatively to actions of hole k
-}
-
-\begin{multline*}
-\forall s_1\in S,\, \forall \OTx{1}{a}{1}{1}, \OTx{1}{b}{2}{2} \in \fOT{s_1}.\\
-\neg\left(\alpha_{1 a} = \alpha_{1 b}\land s'_{1 a}\neq s'_{1 b}\land g_{1 a}\land g_{1 b} \land\beta_{1 k} \neq \beta_{2 k}\right)
-\end{multline*}
-
-An composable automaton cannot transform external non-determinism of the sub-automaton into internal non-determinism.
-
-This creates a conflict between deadlock reduction and the properties involving composition.
+%\TODO{add a notion of composable at hole i:
+%An OA is composable at hole k if it is partially deterministic relatively to actions of hole k
+%}
+%
+%
+%\begin{multline*}
+%\forall s_1\in S,\, \forall \OTx{1}{a}{1}{1}, \OTx{1}{b}{2}{2} \in \fOT{s_1}.\\
+%\neg\left(\alpha_{1 a} = \alpha_{1 b}\land s'_{1 a}\neq s'_{1 b}\land g_{1 a}\land g_{1 b} \land\beta_{1 k} \neq \beta_{2 k}\right)
+%\end{multline*}
+%
+%An composable automaton cannot transform external non-determinism of the sub-automaton into internal non-determinism.
+
+%This creates a conflict between deadlock reduction and the properties involving composition.
 One possible solution to avoid this conflict is to only consider a composition that do not introduce deadlocks, we will define such a composition below.
-But before defining non-blocking composition, we first introduce a notion of state reachability for open automata. 
-\begin{definition}[Reachability] \label{Def:Reach}
-For any open automata \(A = \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is any predicate on states that is valid on initial state, and preserved across transitions:
-\[\sigma_0 \vdash \reach{A}\mpar{s_0}\quad\land\quad\forall t = \OTg \in T, \fvars{t} \vdash \left(\reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}\right)\]
+%But before defining non-blocking composition, we first introduce a notion of state reachability for open automata.
+
+%
+%\begin{definition}[Non-blocking composition]\label{Def:Non-blockcomp}
+%Let \(A_i = \OAg[i]\) with \( 0 \leq i \leq n\) be a family of open automata.
+%Let \(A = A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) and $A= \OAg$.
+%
+%The composition \(A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is non-blocking if   \(A \) has a reachability predicate such that, for each reachable configuration, if there is a possible transition in \(A_0\) then there is a possible transition in \(A\):
+%\[ \forall s = \mpar{s_0, s_1,..,s_n} \in S, V \uplus \biguplus_\subbox{t_0 \in \fOT{s_0}} \fvars{t_0} \vdash \left(\reach{A}\mpar{s} \wedge \bigvee_\subbox{t_0 \in \fOT{s_0}} \fguard{t_0} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \right)\]
+%\end{definition}
+%Again we use guards to ensure that the transition can occur. It is not sufficient to ensure the existence of equivalent transitions in general, but it will be sufficient in the context of refinement.
+
+We first define when a relation is preserved along identical transition deadlock reducing, before characterising a first simple refinement relation  to compare automata with identical holes.
+
+%\subsection{Deadlock Reduction, Reachability, and Composition}
+\TODO{rewrite}
+A notion that is often used in the context of refinement is the notion of deadlock reduction.
+This property considers that two states related by a given relation and states that if one state can do a transition, then the other can do a transition too.
+This notion is not much interesting in the general case as there is a priori no relation between the two transitions.
+However, when the relation that relates states is a simulation, this will relate the possible transitions and the deadlock reduction will become a valuable property.
+%
+%Next definition states that if $T_2$ is not in a deadlock position then $T_1$ can do a transition but not necessarily with the same input values.
+This is very weak but sufficient when composed with the def  of simulation.
+
+%\begin{definition}[Preservation along identical transitions]\label{def:preservation} \\
+%Let \(\OAg[1]\) and \(\OAg[2]\) be two OAs.
+%A relation \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) between  \(\OAg[1]\) and \(\OAg[2]\)
+%  is preserved along identical transitions if  it satisfies the following:
+%\begin{multline*}
+%\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_2} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\  V_1 \uplus V_2 \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \implies  R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}\\
+%\end{multline*}
+%\end{definition}
+
+\begin{definition}[Preservation along identical transitions]\label{def:preservation} \\
+Let \(\OAg[1]\) and \(\OAg[2]\) be two OAs.
+A relation \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) between  \(\OAg[1]\) and \(\OAg[2]\)
+  is preserved along identical transitions if  it satisfies the following:
+\begin{multline*}
+\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_2} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\ 
+\exists 
+\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},
+ V_1 \uplus V_2 \uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 
+%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} 
+\implies \\
+%\exists
+%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
+\bigwedge_{x\in X}
+\mpar{
+\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_2 \land \bigwedge_\subbox{j \in J'_2 } \beta_{2j} = \beta_{1xj}\land g_{1 x}\land
+ R\mpar{s'_{1 x}, s'_2}\psubst{\psi_{1 x} \uplus \psi_2}}\\
+\end{multline*}
 \end{definition}
-Reachability takes into account all paths, and can over-approximate the reachable configurations. 
-From an automation point of view, finding the most precise reachability predicate for a given automata is not decidable because of the symbolic nature of open automata, but only an over-approximation is necessary.
-An automatic tool would only need to find an over approximation of reachability to reason on composition that is compatible with deadlock reduction.
-We call \emph{non-blocking composition} a composition that can be safely be used to compose open automata that are involved in a deadlock reducing relation.
-
-\begin{definition}[Non-blocking composition]\label{Def:Non-blockcomp}
-Let \(A_i = \OAg[i]\) with \( 0 \leq i \leq n\) be a family of open automata.
-Let \(A = A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) and $A= \OAg$.
-
-The composition \(A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is non-blocking if   \(A \) has a reachability predicate such that, for each reachable configuration, if there is a possible transition in \(A_0\) then there is a possible transition in \(A\):
-\[ \forall s = \mpar{s_0, s_1,..,s_n} \in S, V \uplus \biguplus_\subbox{t_0 \in \fOT{s_0}} \fvars{t_0} \vdash \left(\reach{A}\mpar{s} \wedge \bigvee_\subbox{t_0 \in \fOT{s_0}} \fguard{t_0} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \right)\]
-\end{definition}
-Again we use guards to ensure that the transition can occur. It is not sufficient to ensure the existence of equivalent transitions in general, but it will be sufficient in the context of refinement.
-
-\subsection{Refinement Relations for automata with the same holes}
+
+\medskip
 
@@
 Let $J_3$ be the set of holes of $A_3$.
-Suppose that \(k \in H\) and that \(A_1\subst{A_3}{k}\) is non-blocking.
+%Suppose that \(k \in H\) and that \(A_1\subst{A_3}{k}\) is non-blocking.
 We have: \[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{J_3 \uplus H \setminus \mbrc{k}}\]
@@
 Let $A_1$, $A_2$ and $A_3$ be three open automata with $\wrel{A_2}{A_3}{H}$. 
-Suppose that \(k \in H\) and that \(A_1\subst{A_2}{k}\) is non-blocking.
+%Suppose that \(k \in H\) and that \(A_1\subst{A_2}{k}\) is non-blocking.
 We have: \[\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{J_1 \uplus H \setminus \mbrc{k}}\]
@@
 \paragraph{First case: Both automata perform a transition.}
-The transition $t_{13}$ is obtained by the composition of  transitions $t_1=\OTx{1}{}{1}{1}$ and  \[t_3^1=
-\OT{ s^1_3}{{s^1_3}'}{\alpha_3^1}{   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{ g^1_3 }{ \psi^1_3} \qquad \text{ when } k \in J'_{1} 
+The transition $t_{13}$ is obtained by the composition of  transitions $t_1=\OTx{1}{}{1}{1}\in \fOT{s_1}$ and  \[t_3^1=
+\OT{ s^1_3}{{s^1_3}'}{\alpha_3^1}{   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{ g^1_3 }{ \psi^1_3}\in \fOT{s^1_3} \qquad \text{ when } k \in J'_{1} 
 \] The result is:
@@
 
-\item The last formula we need to prove is that the relation is preserved along identical transitions, i.e. the following is satisfied 
+\item The last formula we need to prove is that the relation is preserved along identical transitions, i.e.
+the following is satisfied (we define $V_{13} = V_1 \uplus V_3$ and $ V_{23} = V_2\uplus V_3$)
+
+\begin{multline*}
+\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}, \bigsymb{\forall} \mpar{t_{13}, t_{23}} = \mpar{\OTx{13}{}{13}{13}, \OTx{23}{}{23}{23}} \in \fOT{s_{13}} \times \fOT{s_{23}} \\  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} \vdash \hspace{6cm}\\  R\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23}
+\implies 
+\exists
+\OT{s_{13}}{s'_{13a}}{\alpha_{13a}}{\beta_{13aj}^{j \in J'_{13a}}}{g_{13a}}{\psi_{13a}}\in \fOT{s_{13}}.\\ \alpha_{13}=\alpha_{1 3a} \land
+J'_{13a}  = J'_{23} \land g_{1 3a} \land \bigwedge_\subbox{j \in  J'_{23}} \beta_{12j} = \beta_{13aj}\land
+ R\mpar{s'_{1 3a}, s'_{23}}\psubst{\psi_{1 3a} \uplus \psi_{23}}\\
+\end{multline*}
+
+We pick $s_{13}$, $s'_{13a}$, and two open transitions $t_{13}$ and $t_{23}$.
+Where $s_{13}=(s_1,s_3)$ and $s_{23}=(s_2,s_3)$ by construction of $R$.
+
+We reason on the way the OT $t_{23}$ has been obtained: either the hole $k$ of A2 is involved in the transition or not.
+
+\paragraph{First case: Both A2 and A3 are involved in transition $t_{23}$.}
+The transition $t_{23}$ is obtained by the composition of  transitions $t_2=\OTx{2}{}{2}{2}\in\fOT{s_2}$ and  \[t_3^2=
+\OT{ s_3}{{s^2_3}'}{\alpha_3^2}{   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }}{ g^2_3 }{ \psi^2_3}\in\fOT{s_3} \qquad \text{ when } k \in J'_{2} 
+\] The result is:
+\[
+t_{23} = \OT{\mpar{s_2, s_3}}{\mpar{s'_2, {s^2_3}'}}{\alpha_2}{\beta_{2j}^{j \in J'_2 \setminus \{k\}} \uplus  {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }}{g_2 \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k}}{\psi_2 \uplus \psi^2_3} \qquad \text{ where } k \in J'_{2}
+\]
+
+Two cases are possible for $t_{13}$: either the hole $k$ of A1 is involved in the transition or not.
+
+$\bullet$ if  the hole $k$ of A1 is involved in the transition: 
+The transition $t_{13}$ is obtained by the composition of  transitions $t_1=\OTx{1}{}{1}{1}\in\fOT{s_1}$ and  \[t_3^1=
+\OT{ s_3}{{s^1_3}'}{\alpha_3^1}{   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{ g^1_3 }{ \psi^1_3} \qquad \text{ when } k \in J'_{1} 
+\] The result is:
+\[
+t_{13} = \OT{\mpar{s_1, s_3}}{\mpar{s'_1, {s^1_3}'}}{\alpha_1}{\beta_{1j}^{j \in J'_1 \setminus \{k\}} \uplus  {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{g_1 \wedge g^1_3 \wedge \alpha^1_3 = \beta_{1k}}{\psi_1 \uplus \psi^1_3} \qquad \text{ where } k \in J'_{1}
+\]
+
+$\bullet$ if  the hole $k$ of A1 is not involved in the transition:
+$t_1=\OTx{1}{}{1}{1}$ when  $k \not\in J'_{1} $
+and 
+\[
+t_{13} = \OT{\mpar{s_1, s_3}}{\mpar{s'_1, {s_3}}}{\alpha_1}{\beta_{1j}^{j \in J'_1}}{g_1}{\psi_1}
+\]
+
+\smallskip
+In both cases note that $g_{13} \implies g_1$, with  $\mpar{s_1, s_2} \in S_1 \times S_2$, Definition~\ref{def:preservation} applied to OTs $t_1,\,t_2$ gives the following:
+
+\begin{multline*}
+  V_1 \uplus V_2 \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 
+%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} 
+\implies \\
+\exists
+\OT{s_1}{s_4}{\alpha_4}{\beta_{4j}^{j \in J'_4}}{g_4}{\psi_4}\in \fOT{s_1}. \alpha_1=\alpha_{4} \land J'_4 =J'_2 \land g_{4} \land \bigwedge_\subbox{j \in J'_2} \beta_{2j} = \beta_{4j}\land
+ R\mpar{s'_{4}, s'_2}\psubst{\psi_{4} \uplus \psi_2}\\
+\end{multline*}
+
+We reason on such a $t_1'=\OT{s_1}{s_4}{\alpha_4}{\beta_{4j}^{j \in J'_4}}{g_4}{\psi_4}\in \fOT{s_1}$ to obtain a new open transition of A1 and compose it with $t_3^2$
+
+We obtain 
+\[
+t_{13}' = \OT{\mpar{s_1, s_3}}{\mpar{s_4, {s_3}}}{\alpha_4}{\beta_{4j}^{j \in J'_4 \setminus \{k\}} \uplus  {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }}{g_4 \wedge g^2_3 \wedge \alpha^2_3 = \beta_{4k}}{\psi_4 \uplus \psi^2_3} \qquad \text{ where } k \in J'_{4}
+\]
+
+ON REVIENT A NOTRE BUT INITIAL
+ON VEUT:
+\begin{multline*}
+  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} \vdash \hspace{6cm}\\  R\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
+\implies 
+\exists
+\OT{s_{13}}{s'_{13a}}{\alpha_{13a}}{\beta_{13aj}^{j \in J'_{13a}}}{g_{13a}}{\psi_{13a}}\in \fOT{s_{13}}.\\ \alpha_{13}=\alpha_{1 3a} \land
+J'_{13a}  = J'_{23} \land g_{1 3a} \land \bigwedge_\subbox{j \in  J'_{23}} \beta_{12j} = \beta_{13aj}\land
+ R\mpar{s'_{1 3a}, s'_{23}}\psubst{\psi_{1 3a} \uplus \psi_{23}}\\
+\end{multline*}
+
 \TODO{NEW PROOF SKETCH}

### 2022-06-09 2021-Refinement/paper/refinementarticle.tex
more proof

@@
 \mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},
- V_1 \uplus V_2 \uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 
+ V_1 \uplus V_2 \uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_2} \uplus \fvars{t_1} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 
 %\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} 
@@
 \begin{multline*}
-\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}, \bigsymb{\forall} \mpar{t_{13}, t_{23}} = \mpar{\OTx{13}{}{13}{13}, \OTx{23}{}{23}{23}} \in \fOT{s_{13}} \times \fOT{s_{23}} \\  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} \vdash \hspace{6cm}\\  R\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23}
+\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}, \bigsymb{\forall} \mpar{t_{13}, t_{23}} = \mpar{\OTx{13}{}{13}{13}, \OTx{23}{}{23}{23}} \in \fOT{s_{13}} \times \fOT{s_{23}} \\ 
+\exists 
+\mpar{t_{13x} = \OTx{13}{x}{13x}{13x} \in \fOT{s_{13}}}^{x \in X},\\
+ V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
+\vdash \hspace{6cm}\\  R\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
 \implies 
-\exists
-\OT{s_{13}}{s'_{13a}}{\alpha_{13a}}{\beta_{13aj}^{j \in J'_{13a}}}{g_{13a}}{\psi_{13a}}\in \fOT{s_{13}}.\\ \alpha_{13}=\alpha_{1 3a} \land
-J'_{13a}  = J'_{23} \land g_{1 3a} \land \bigwedge_\subbox{j \in  J'_{23}} \beta_{12j} = \beta_{13aj}\land
- R\mpar{s'_{1 3a}, s'_{23}}\psubst{\psi_{1 3a} \uplus \psi_{23}}\\
+\bigwedge_{x\in X}
+\mpar{
+ \alpha_{13}=\alpha_{1 3x} \land
+J'_{13x}  = J'_{23}  \land \bigwedge_\subbox{j \in  J'_{23}} \beta_{23j} = \beta_{13xj}\land g_{1 3x} \land
+ R\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 3x} \uplus \psi_{23}}}
 \end{multline*}
@@
 \begin{multline*}
-  V_1 \uplus V_2 \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 
+\exists 
+\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},
+  V_1 \uplus V_2 \uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 
 %\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} 
 \implies \\
-\exists
-\OT{s_1}{s_4}{\alpha_4}{\beta_{4j}^{j \in J'_4}}{g_4}{\psi_4}\in \fOT{s_1}. \alpha_1=\alpha_{4} \land J'_4 =J'_2 \land g_{4} \land \bigwedge_\subbox{j \in J'_2} \beta_{2j} = \beta_{4j}\land
- R\mpar{s'_{4}, s'_2}\psubst{\psi_{4} \uplus \psi_2}\\
-\end{multline*}
-
-We reason on such a $t_1'=\OT{s_1}{s_4}{\alpha_4}{\beta_{4j}^{j \in J'_4}}{g_4}{\psi_4}\in \fOT{s_1}$ to obtain a new open transition of A1 and compose it with $t_3^2$
+\bigwedge_{x\in X}
+\mpar{
+\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_2 \land \bigwedge_\subbox{j \in J'_2 } \beta_{2j} = \beta_{1xj}\land g_{1 x}\land
+ R\mpar{s'_{1 x}, s'_2}\psubst{\psi_{1 x} \uplus \psi_2}}
+\end{multline*}
+
+Consider one $t_{1x}=\OT{s_1}{s_{1x}}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x}}}{g_{1x}}{\psi_{1x}}\in \fOT{s_1}$ to obtain a new open transition of A1 and compose it with $t_3^2$
 
@@
 \[
-t_{13}' = \OT{\mpar{s_1, s_3}}{\mpar{s_4, {s_3}}}{\alpha_4}{\beta_{4j}^{j \in J'_4 \setminus \{k\}} \uplus  {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }}{g_4 \wedge g^2_3 \wedge \alpha^2_3 = \beta_{4k}}{\psi_4 \uplus \psi^2_3} \qquad \text{ where } k \in J'_{4}
+t_{13x}' = \OT{\mpar{s_1, s_3}}{\mpar{s_{1x}, {s_3}}}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x} \setminus \{k\}} \uplus  {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }}{g_{1x} \wedge g^2_3 \wedge \alpha^2_3 = \beta_{1xk}}{\psi_{1x} \uplus \psi^2_3} \qquad \text{ where } k \in J'_{1x}
 \]
 
-ON REVIENT A NOTRE BUT INITIAL
-ON VEUT:
-\begin{multline*}
-  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} \vdash \hspace{6cm}\\  R\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
+This specifies the family $\mpar{t_{13x}'}^{x\in X}$
+
+ON REVIENT A NOTRE BUT INITIAL et ON A
+\begin{multline*}
+  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
+\vdash \hspace{6cm}\\  R\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
 \implies 
-\exists
-\OT{s_{13}}{s'_{13a}}{\alpha_{13a}}{\beta_{13aj}^{j \in J'_{13a}}}{g_{13a}}{\psi_{13a}}\in \fOT{s_{13}}.\\ \alpha_{13}=\alpha_{1 3a} \land
-J'_{13a}  = J'_{23} \land g_{1 3a} \land \bigwedge_\subbox{j \in  J'_{23}} \beta_{12j} = \beta_{13aj}\land
- R\mpar{s'_{1 3a}, s'_{23}}\psubst{\psi_{1 3a} \uplus \psi_{23}}\\
-\end{multline*}
+ R\mpar{s_{1}, s_{2}} \wedge 	g_{1} \wedge g_2 \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} \wedge \alpha_{1} = \alpha_{2} 
+\end{multline*}
+
+\begin{multline*}
+  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
+\vdash \hspace{6cm}\\  R\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
+\implies 
+\bigwedge_{x\in X}
+\big(
+ \alpha_{13}=\alpha_1=\alpha_{1 x}  \land J'_{1x}\uplus J'_3= J'_2\uplus J'_3\\
+ \land \bigwedge_\subbox{j \in J'_2 \setminus\{k\} } \beta_{2j} = \beta_{1xj}
+ \land \bigwedge_\subbox{j \in {j \in J^{2 \prime}_3} }  (\beta^2_{3j}) = (\beta^2_{3j}) \land g_{1 x}\land
+ R\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 x} \uplus \psi_2}\big)
+\wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} = \beta_{1xk}
+\end{multline*}
+Finally , because $R\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 x} \uplus \psi_2} \implies R\mpar{s'_{1 3x}, s'_{23}}\psubst{(\psi_{1 x} \uplus \psi^2_3) \uplus (\psi_2 \uplus \psi^2_3)}$
+\begin{multline*}
+  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
+\vdash \hspace{6cm}\\  R\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
+\implies 
+\bigwedge_{x\in X}
+\mpar{
+ \alpha_{13}=\alpha_{1 3x} \land
+J'_{13x}  = J'_{23}  \land \bigwedge_\subbox{j \in  J'_{23}} \beta_{23j} = \beta_{13xj}\land g_{1 3x} \land
+ R\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 3x} \uplus \psi_{23}}}
+\end{multline*}
+
+This concludes for the current case.
 

### 2022-06-09 2021-Refinement/paper/refinementarticle.tex
title case 2
a bit of comments and orga in proof

@@
 \vdash \hspace{6cm}\\  R\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
-\implies 
+\implies \\
 \bigwedge_{x\in X}
@@
 \smallskip
-In both cases note that $g_{13} \implies g_1$, with  $\mpar{s_1, s_2} \in S_1 \times S_2$, Definition~\ref{def:preservation} applied to OTs $t_1,\,t_2$ gives the following:
+In both cases note that $g_{13} \implies g_1$, with  $\mpar{s_1, s_2} \in S_1 \times S_2$, Definition~\ref{def:preservation} applied to OTs $t_1,\,t_2$ gives the following property that we denote ($\star$):
 
@@
 \exists 
-\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},
+\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},\\
   V_1 \uplus V_2 \uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 
@@
 This specifies the family $\mpar{t_{13x}'}^{x\in X}$
-
-ON REVIENT A NOTRE BUT INITIAL et ON A
+that allows us to prove the initial goal, i.e. the relation is preserved along identical transitions. We derive from the property ($\star$) and from the definition of $t_{13x}'$ and $t_{23}$
 \begin{multline*}
@@
 This concludes for the current case.
+
+\paragraph{second case: Only A2 is involved in transition $t_{23}$.}
 

### 2022-06-10 2021-Refinement/paper/refinementarticle.tex
minor
REMOVE reachability

@@
 \usepackage{nccrules}
+\usepackage{comment}
 
@@
 This aspect is also present in open automata.
-They show how invariants, a notion near to our reachability predicates, are composed.
+They show how invariants are composed.
 By relation on these invariants they introduce several refinement relations.
@@
 We define a relation $R'$ relating states of $s_{13}$ and $s_{23}$ as follows:
-\[ R' \mpar{s_{13}, s_{23}} = R\mpar{s_{1}, s_{2}} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigwedge_\subbox{v_3\in V_3}
+\[ R' \mpar{s_{13}, s_{23}} = R\mpar{s_{1}, s_{2}}  %\wedge \reach{A_{13}}\mpar{s_{13}}
+ \wedge \bigwedge_\subbox{v_3\in V_3}
  v^1_3=v^2_3\wedge s^1_3 = s^2_3\]
+
+%\TODO{[Ludo] I believe reachability is not useful here -- to check}
 
@@
 with $\sigma_{013} = \sigma_{01} \uplus \sigma_{03}^1$, $\sigma_{023} = \sigma_{02} \uplus \sigma_{03}^2$, $s_{013}=(s_{01},s_{03}^1)$, and $s_{023}=(s_{02},s_{02}^2)$.\\
-By using the fact that $R$ relates initial configurations of  $A_1$ and $A_2$, we have  the following statement:
-$\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}}$,  and based on the  fact that initial states are reachable $\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ we have 
-\[ \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
-\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\]
+By using the fact that $R$ relates initial configurations of  $A_1$ and $A_2$, we have:
+$\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}}$.  
+%and based on the  fact that initial states are reachable $\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ we have 
+%\[ \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
+%\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\]
 
@@
 \begin{align*}
-& \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
-\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\\
-\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}} \wedge \reach{A_{13}}\mpar{s_{013}} \psubst{\sigma_{013}} \land \mpar{\,\,\bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }\\
-\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge \reach{A_{13}}\mpar{s_{013}}  \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma^1_{03}\uplus \sigma^2_{03}\uplus \sigma_{013} }\\
+& \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} 
+%\wedge \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}
+\\
+\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}}  \land \mpar{\,\,\bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }\\
+\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge  \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma^1_{03}\uplus \sigma^2_{03}\uplus \sigma_{013} }\\
 \implies & \sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}
@@
 \end{multline*}
-And finally by hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,   by definition of reachability (Definition \ref{Def:Reach}) we obtain $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
-\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
-Thus, we get:
-\begin{multline*}
-V_{13} \uplus V_{23} \uplus  \fvars{t_{13}} \vdash\\
-R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \reach{A_{13}}\mpar{s_{13}}
-\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
-\implies \hspace{5em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge 	g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\\
-		  \wedge \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
-\wedge \bigwedge_\subbox{v_3\in V_3}  \psi_{13}(v^1_3)=\psi_{13}(v^2_3)\wedge s^{1\prime}_3=s^{2\prime}_3
-		\end{array}}   
-\end{multline*}	
+%And finally by hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,   by definition of reachability (Definition \ref{Def:Reach}) we obtain $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
+%\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
+%Thus, we get:
+%\begin{multline*}
+%V_{13} \uplus V_{23} \uplus  \fvars{t_{13}} \vdash\\
+%R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \reach{A_{13}}\mpar{s_{13}}
+%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
+%\implies \hspace{5em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+%\begin{array}{l}
+%			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge 	g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\\
+%		  \wedge \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
+%\wedge \bigwedge_\subbox{v_3\in V_3}  \psi_{13}(v^1_3)=\psi_{13}(v^2_3)\wedge s^{1\prime}_3=s^{2\prime}_3
+%		\end{array}}   
+%\end{multline*}	
 Because of the independence of the substitution domains, we simplify and get the expected formula:
@@
 
-\paragraph{second case: Only A2 is involved in transition $t_{23}$.}
+\paragraph{Second case: Only A2 is involved in transition $t_{23}$.}
 
@@
 \TODO{END OF NEW PROOF SKETCH}
+\begin{comment}
  $\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$ and
@@
 % \end{enumerate}
+
+\end{comment}
 

### 2022-06-10 2021-Refinement/paper/refinementarticle.tex
first draft exalanation

@@
 A notion that is often used in the context of refinement is the notion of deadlock reduction.
-This property considers that two states related by a given relation and states that if one state can do a transition, then the other can do a transition too.
-This notion is not much interesting in the general case as there is a priori no relation between the two transitions.
-However, when the relation that relates states is a simulation, this will relate the possible transitions and the deadlock reduction will become a valuable property.
+The objective i that two states related by a given relation and states that if one state can do a transition, then the other can do a transition too.
+What raises this difficulty is the fact that the automaton that simulates a specification features any behaviour that contains the behaviour of the specification but this is only verified at each state of the automaton.
+In this definition, nothing prevents the implementation from adding non-determinism and non-deterministically reaching a deadlock that does not exist in the specification.
+The idea is that simulation states that there is a relation between states such that, for related states, the behaviour of the implementation must follow the behaviour of the specification ...
+but also when both the implementation and the specification do the same transition, they stay related.
+This ensures a form of continuity in the comparison in the sense that the refined system is constrained to follow the behaviour of the simulated system along a given scenario. 
+In terms of traces this amounts to some form of deadlock reduction: for each trace followed by the simulated system if the refined system followed the beginning of the trace, it must be able to keep following the trace.
+Except that the notion of trace is insufficient to characterize a scenario of execution in OAs because of the presence of guards, states, and holes.
+
 %

### 2022-06-15 2021-Refinement/paper/refinementarticle.tex
tentative de poursuivre

@@
 \forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_2} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\ 
-\exists 
+\bigexists 
 \mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},
@@
 \item The last formula we need to prove is that the relation is preserved along identical transitions, i.e.
-the following is satisfied (we define $V_{13} = V_1 \uplus V_3$ and $ V_{23} = V_2\uplus V_3$)
+the following is satisfied (we define $V_{13} = V_1 \uplus V_3$ and $ V_{23} = V_2\uplus V_3$):
 
@@
 \forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}, \bigsymb{\forall} \mpar{t_{13}, t_{23}} = \mpar{\OTx{13}{}{13}{13}, \OTx{23}{}{23}{23}} \in \fOT{s_{13}} \times \fOT{s_{23}} \\ 
-\exists 
+\bigexists 
 \mpar{t_{13x} = \OTx{13}{x}{13x}{13x} \in \fOT{s_{13}}}^{x \in X},\\
@@
 
-We reason on the way the OT $t_{23}$ has been obtained: either the hole $k$ of A2 is involved in the transition or not.
-
-\paragraph{First case: Both A2 and A3 are involved in transition $t_{23}$.}
+We reason on the way the OT $t_{23}$ has been obtained: either the hole $k$ of $A_2$ is involved in the transition or not.
+
+\paragraph{First case: Both $A_2$ and $A_3$ are involved in transition $t_{23}$.}
 The transition $t_{23}$ is obtained by the composition of  transitions $t_2=\OTx{2}{}{2}{2}\in\fOT{s_2}$ and  \[t_3^2=
@@
 
-Two cases are possible for $t_{13}$: either the hole $k$ of A1 is involved in the transition or not.
-
-$\bullet$ if  the hole $k$ of A1 is involved in the transition: 
+Two cases are possible for $t_{13}$: either the hole $k$ of $A_1$ is involved in the transition or not.
+
+$\bullet$ if  the hole $k$ of $A_1$ is involved in the transition: 
 The transition $t_{13}$ is obtained by the composition of  transitions $t_1=\OTx{1}{}{1}{1}\in\fOT{s_1}$ and  \[t_3^1=
@@
 \begin{multline*}
-\exists 
+\bigexists 
 \mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},\\
@@
 
-\paragraph{Second case: Only A2 is involved in transition $t_{23}$.}
+\paragraph{Second case: Only $A_2$ is involved in transition $t_{23}$.}
+$t_{23}$ is obtained  by  the transition $t_2=\OTx{2}{}{2}{2}$ alone with the state $s^2_3$ unchanged, if $k \not\in J_2'$
+\[t_{23} = \OT{\mpar{s_2, s^2_3}}{\mpar{s'_2, s^2_3}}{\alpha_2}{\beta_{2j}^{j \in J'_2}}{g_1}{\psi_2}
+\]
+-----------------------------\\
+As in the previous case, two cases are possible for $t_{13}$: either the hole $k$ of $A_1$ is involved in the transition or not.
+
+$\bullet$ if  the hole $k$ of $A_1$ is involved in the transition: 
+The transition $t_{13}$ is obtained by the composition of  transitions $t_1=\OTx{1}{}{1}{1}\in\fOT{s_1}$ and  \[t_3^1=
+\OT{ s_3}{{s^1_3}'}{\alpha_3^1}{   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{ g^1_3 }{ \psi^1_3} \qquad \text{ when } k \in J'_{1} 
+\] The result is:
+\[
+t_{13} = \OT{\mpar{s_1, s_3}}{\mpar{s'_1, {s^1_3}'}}{\alpha_1}{\beta_{1j}^{j \in J'_1 \setminus \{k\}} \uplus  {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{g_1 \wedge g^1_3 \wedge \alpha^1_3 = \beta_{1k}}{\psi_1 \uplus \psi^1_3} \qquad \text{ where } k \in J'_{1}
+\]
+
+$\bullet$ if  the hole $k$ of $A_1$ is not involved in the transition:
+$t_1=\OTx{1}{}{1}{1}$ when  $k \not\in J'_{1} $
+and 
+\[
+t_{13} = \OT{\mpar{s_1, s_3}}{\mpar{s'_1, {s_3}}}{\alpha_1}{\beta_{1j}^{j \in J'_1}}{g_1}{\psi_1}
+\]
+
+In both cases note that $g_{13} \implies g_1$, with  $\mpar{s_1, s_2} \in S_1 \times S_2$, Definition~\ref{def:preservation} applied to OTs $t_1,\,t_2$ gives the following property that we denote ($\star$):
+
+\begin{multline*}
+\bigexists 
+\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},\\
+  V_1 \uplus V_2 \uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 
+%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} 
+\implies \\
+\bigwedge_{x\in X}
+\mpar{
+\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_2 \land \bigwedge_\subbox{j \in J'_2 } \beta_{2j} = \beta_{1xj}\land g_{1 x}\land
+ R\mpar{s'_{1 x}, s'_2}\psubst{\psi_{1 x} \uplus \psi_2}}
+\end{multline*}
+
+Consider one $t_{1x}=\OT{s_1}{s_{1x}}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x}}}{g_{1x}}{\psi_{1x}}\in \fOT{s_1}$ to obtain a new open transition of $A_1$    with the state $s^2_3$ unchanged, since $J'_{1x} = J_2'$ and $k \not\in J_2'$.
+
+We obtain
+
+\[t_{13x}=\OT{(s_1,s^2_3)}{(s_{1x},s^2_3)}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x}}}{g_{1x}}{\psi_{1x}}\]
+
+-------------------------------\\
 

### 2022-06-16 2021-Refinement/paper/refinementarticle.tex
note?

@@
 
-In both cases note that $g_{13} \implies g_1$, with  $\mpar{s_1, s_2} \in S_1 \times S_2$, Definition~\ref{def:preservation} applied to OTs $t_1,\,t_2$ gives the following property that we denote ($\star$):
+In both cases note that $g_{13} \implies g_1$\TODO{equal?}, with  $\mpar{s_1, s_2} \in S_1 \times S_2$, Definition~\ref{def:preservation} applied to OTs $t_1,\,t_2$ gives the following property that we denote ($\star$):
 

### 2022-06-16 2021-Refinement/paper/refinementarticle.tex
R'

--- 2022-06-15 2021-Refinement/paper/refinementarticle.tex
@@
 
-Consider one $t_{1x}=\OT{s_1}{s_{1x}}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x}}}{g_{1x}}{\psi_{1x}}\in \fOT{s_1}$ to obtain a new open transition of A1 and compose it with $t_3^2$
-
+Consider one $t_{1x}=\OT{s_1}{s_{1x}}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x}}}{g_{1x}}{\psi_{1x}}\in \fOT{s_1}$ to obtain a new open transition of A1 and compose it with $t_3^2$.
 We obtain 
@@
   V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
-\vdash \hspace{6cm}\\  R\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
-\implies 
- R\mpar{s_{1}, s_{2}} \wedge 	g_{1} \wedge g_2 \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} \wedge \alpha_{1} = \alpha_{2} 
+\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
+\implies \\
+ R\mpar{s_{1}, s_{2}} \wedge 	g_{1} \wedge g_2 \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} \wedge \alpha_{1} = \alpha_{2} \bigwedge_\subbox{v_3\in V_3}
+ v^1_3=v^2_3\wedge s^1_3 = s^2_3
 \end{multline*}
@@
   V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
-\vdash \hspace{6cm}\\  R\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
+\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
 \implies 
@@
  \land \bigwedge_\subbox{j \in {j \in J^{2 \prime}_3} }  (\beta^2_{3j}) = (\beta^2_{3j}) \land g_{1 x}\land
- R\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 x} \uplus \psi_2}\big)
+ R'\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 x} \uplus \psi_2}\big)
 \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} = \beta_{1xk}
 \end{multline*}
-Finally , because $R\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 x} \uplus \psi_2} \implies R\mpar{s'_{1 3x}, s'_{23}}\psubst{(\psi_{1 x} \uplus \psi^2_3) \uplus (\psi_2 \uplus \psi^2_3)}$
+Finally , because $R'\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 x} \uplus \psi_2} \implies R\mpar{s'_{1 3x}, s'_{23}}\psubst{(\psi_{1 x} \uplus \psi^2_3) \uplus (\psi_2 \uplus \psi^2_3)}$
 \begin{multline*}
   V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
-\vdash \hspace{6cm}\\  R\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
+\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
 \implies \\
@@
 J'_{13x}  = J'_{23}  \land \bigwedge_\subbox{j \in  J'_{23}} \beta_{23j} = \beta_{13xj}\land g_{1 3x} \land
- R\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 3x} \uplus \psi_{23}}}
+ R'\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 3x} \uplus \psi_{23}}}
 \end{multline*}

### 2022-06-17 2021-Refinement/paper/refinementarticle.tex
meeting : add again deterministic composition
proof trans

@@
 
-%\TODO{add a notion of composable at hole i:
-%An OA is composable at hole k if it is partially deterministic relatively to actions of hole k
-%}
-%
-%
-%\begin{multline*}
-%\forall s_1\in S,\, \forall \OTx{1}{a}{1}{1}, \OTx{1}{b}{2}{2} \in \fOT{s_1}.\\
-%\neg\left(\alpha_{1 a} = \alpha_{1 b}\land s'_{1 a}\neq s'_{1 b}\land g_{1 a}\land g_{1 b} \land\beta_{1 k} \neq \beta_{2 k}\right)
-%\end{multline*}
-%
-%An composable automaton cannot transform external non-determinism of the sub-automaton into internal non-determinism.
+\TODO{add a notion of composable at hole i:
+An OA is composable at hole k if it is partially deterministic relatively to actions of hole k
+}
+
+\begin{multline*}
+\forall s_1\in S,\, \forall \OTx{1}{a}{1}{1}, \OTx{1}{b}{2}{2} \in \fOT{s_1}.\\
+\neg\left(\alpha_{1 a} = \alpha_{1 b}\land g_{1 a}\land g_{1 b} \land\beta_{1 k} \neq \beta_{2 k}\right)
+\end{multline*}
+
+An composable automaton cannot transform external non-determinism of the sub-automaton into internal non-determinism.
 
@@
 \forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_2} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\ 
-\bigexists 
+\bigsymb{\bigexists} 
 \mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},
@@
 %\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
-\bigwedge_{x\in X}
+\bigsymb{\bigwedge_{x\in X}}
 \mpar{
@@
 \item  Finally, we have to prove the following holds:
+\begin{multline*}
+\forall \mpar{s_1, s_3} \in S_1 \times S_3, \bigsymb{\forall} \mpar{t_1, t_3} = \mpar{\OTx{1}{}{1}{1}, \OTx{3}{}{3}{3}} \in \fOT{s_1} \times \fOT{s_3} \\ 
+\bigsymb{\bigexists} 
+\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},
+ V_1 \uplus V_3\uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_3} \vdash \hspace{6cm}\\  R\mpar{s_1, s_3} \wedge 	g_1 \wedge g_3 \wedge \alpha_1 = \alpha_3 
+%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_3} \beta_{1j} = \beta_{3j} 
+\implies \hspace{6cm}\\
+%\exists
+%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
+\bigsymb{\bigwedge_{x\in X}}
+\mpar{
+\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{1xj}\land g_{1 x}\land
+ R_{13}\mpar{s'_{1 x}, s'_3}\psubst{\psi_{1 x} \uplus \psi_3}}
+\end{multline*}
+According to the refinement relation between  $A_1$ and $A_2$ we have:
+\begin{multline*}
+\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_2} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\ 
+\bigsymb{\bigexists} 
+\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},
+ V_1 \uplus V_2 \uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 
+%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} 
+\implies \hspace{6cm}\\
+%\exists
+%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
+\bigsymb{\bigwedge_{x\in X}}
+\mpar{
+\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_2 \land \bigwedge_\subbox{j \in J'_2 } \beta_{2j} = \beta_{1xj}\land g_{1 x}\land
+ R_{12}\mpar{s'_{1 x}, s'_2}\psubst{\psi_{1 x} \uplus \psi_2}}
+\end{multline*}
+Yet according to the relation between   $A_2$ and $A_3$ we have:
+
+\begin{multline*}
+\forall \mpar{s_2, s_3} \in S_1 \times S_3, \bigsymb{\forall} \mpar{t_2, t_3} = \mpar{\OTx{2}{}{2}{2}, \OTx{3}{}{3}{3}} \in \fOT{s_2} \times \fOT{s_3} \\ 
+\bigsymb{\bigexists} 
+\mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X},
+V_2 \uplus V_3\uplus \biguplus_{x\in X}\fvars{t_{2x}} \uplus \fvars{t_3} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_2, s_3} \wedge 	g_2 \wedge g_3 \wedge \alpha_2 = \alpha_3 
+%\wedge \bigwedge_\subbox{j \in J'_2 \cap J'_3} \beta_{2j} = \beta_{3j} 
+\implies \\
+%\exists
+%\OTx{1}{a}{3}{3}\in \fOT{s_2}. \\
+\bigsymb{\bigwedge_{x\in X}}
+\mpar{
+\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{1xj}\land g_{1 x}\land
+ R_{13}\mpar{s'_{1 x}, s'_3}\psubst{\psi_{1 x} \uplus \psi_3}}\\
+\end{multline*}
+
+------------------------------
+
 $\forall \mpar{s_1,s_3} \in S_1 \times S_3$, $\bigsymb{\forall} \mpar{t_1,t_2, t_{3}}\!=\! \mpar{\OTx{1}{}{1}{1},\OTx{3}{}{3}{3}}\! \in\! \fOT{s_1} \times \fOT{s_3}$
@@
 \forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}, \bigsymb{\forall} \mpar{t_{13}, t_{23}} = \mpar{\OTx{13}{}{13}{13}, \OTx{23}{}{23}{23}} \in \fOT{s_{13}} \times \fOT{s_{23}} \\ 
-\bigexists 
+\bigsymb{\bigexists} 
 \mpar{t_{13x} = \OTx{13}{x}{13x}{13x} \in \fOT{s_{13}}}^{x \in X},\\
@@
 \implies \\
-\bigwedge_{x\in X}
+\bigsymb{\bigwedge_{x\in X}}
 \mpar{

### 2022-06-17 2021-Refinement/paper/refinementarticle.tex
Thm2 suite

@@
 \end{multline*}
-\medskip
+
 \item  Finally, we have to prove the following holds:
@@
 \mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},
- V_1 \uplus V_3\uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_3} \vdash \hspace{6cm}\\  R\mpar{s_1, s_3} \wedge 	g_1 \wedge g_3 \wedge \alpha_1 = \alpha_3 
+ V_1 \uplus V_3\uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_3} \vdash \hspace{6cm}\\  R_{13}\mpar{s_1, s_3} \wedge 	g_1 \wedge g_3 \wedge \alpha_1 = \alpha_3 
 %\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_3} \beta_{1j} = \beta_{3j} 
@@
 \mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},
- V_1 \uplus V_2 \uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 
+ V_1 \uplus V_2 \uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R_{12}\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 
 %\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} 
@@
 \mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X},
-V_2 \uplus V_3\uplus \biguplus_{x\in X}\fvars{t_{2x}} \uplus \fvars{t_3} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_2, s_3} \wedge 	g_2 \wedge g_3 \wedge \alpha_2 = \alpha_3 
+V_2 \uplus V_3\uplus \biguplus_{x\in X}\fvars{t_{2x}} \uplus \fvars{t_3} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R_{23}\mpar{s_2, s_3} \wedge 	g_2 \wedge g_3 \wedge \alpha_2 = \alpha_3 
 %\wedge \bigwedge_\subbox{j \in J'_2 \cap J'_3} \beta_{2j} = \beta_{3j} 
-\implies \\
+\implies \hspace{6cm}\\
 %\exists
@@
 \mpar{
-\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{1xj}\land g_{1 x}\land
- R_{13}\mpar{s'_{1 x}, s'_3}\psubst{\psi_{1 x} \uplus \psi_3}}\\
-\end{multline*}
-
-------------------------------
-
-$\forall \mpar{s_1,s_3} \in S_1 \times S_3$, $\bigsymb{\forall} \mpar{t_1,t_2, t_{3}}\!=\! \mpar{\OTx{1}{}{1}{1},\OTx{3}{}{3}{3}}\! \in\! \fOT{s_1} \times \fOT{s_3}$
-\begin{multline*}
-V_1 \uplus V_3 \uplus \fvars{t_1}  \uplus \fvars{t_3} \vdash R_{13}\mpar{s_1, s_3} \wedge \\ g_1 \wedge g_{2} \wedge g_{3}
-\wedge \alpha_1 = \alpha_{3}  \wedge \bigwedge_\subbox{j \in J'_1\cap  J'_{3}} \beta_{1j} = \beta_{3j}
- \implies R_{13}\mpar{s'_1, s'_3} \psubst{\psi_1 \uplus \psi_3 } 
-\end{multline*}
-
-According to the refinement relation between  $A_1$ and $A_2$ we have, for all $\mpar{s_1,s_{2}} \in S_1 \times S_2$:
-\begin{multline*}
-\bigsymb{\forall} \mpar{t_1, t_{2}} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\  V_1 \uplus V_2 \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R_{12}\mpar{s_1, s_2} \wedge 	g_1 \wedge g_{2} \wedge \alpha_1 = \alpha_{2} \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2}} \beta_{1j} = \beta_{2j} \implies  R_{12}\mpar{s'_1, s'_{2}}\psubst{\psi_1 \uplus \psi_2}
-\end{multline*}
-
-Yet according to the relation between   $A_2$ and $A_3$ we have  $\forall \mpar{s_2,s_3} \in S_2 \times S_3$ and
-\begin{multline*}
-\bigsymb{\forall} \mpar{t_2, t_{3}} = \mpar{\OTx{2}{}{2}{2}, \OTx{3}{}{3}{3}} \in \fOT{s_2} \times \fOT{s_3} \\  V_2 \uplus V_3 \uplus \fvars{t_2} \uplus \fvars{t_3} \vdash \hspace{6cm}\\  R_{23}\mpar{s_2, s_3} \wedge 	g_2 \wedge g_{3} \wedge \alpha_2 = \alpha_{3} \wedge \bigwedge_\subbox{j \in J'_2 \cap J'_{3}} \beta_{2j} = \beta_{3j} \implies  R_{23}\mpar{s'_2, s'_{3}}\psubst{\psi_2 \uplus \psi_3}
-\end{multline*}
-
-We can make the conjunction of these two formulas.
+\alpha_2=\alpha_{2 x}  \land J'_{2x}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{2xj}\land g_{1 x}\land
+ R_{23}\mpar{s'_{2 x}, s'_3}\psubst{\psi_{2 x} \uplus \psi_3}}\\
+\end{multline*}
+
 For each $s_2 \in S_2$, we remark that  $s_2$  allows to relate $s_1$ and $s_3$ if and only if $R_{12}\mpar{s_1, s_2}\land R_{23}\mpar{s_2, s_3} $. 
-Thus, we get  $\forall \mpar{s_1,s_2,s_3} \in S_1\times S_2 \times S_3$ and $\bigsymb{\forall} \mpar{t_1,t_2, t_{3}}\!=\!
+We can make the conjunction of these two formulas,
+we get  $\forall \mpar{s_1,s_2,s_3} \in S_1\times S_2 \times S_3$ and\\ $\bigsymb{\forall} \mpar{t_1,t_2, t_{3}}\!=\!
 \mpar{\OTx{1}{}{1}{1},\OTx{2}{}{2}{2},\OTx{3}{}{3}{3}}\!
@@
 \begin{multline*}
-V_1\uplus V_2 \uplus V_3 \uplus \fvars{t_1} \uplus \fvars{t_2} \uplus \fvars{t_3} \vdash\\ \left(R_{12}\mpar{s_1, s_2} \wedge   g_1 \wedge g_{2} \wedge \alpha_1 = \alpha_{2} \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2}} \beta_{1j} = \beta_{2j}\right) \wedge \hspace{2.5cm}\\ \mpar{R_{23}\mpar{s_2, s_3}
-\wedge  g_2 \wedge g_{3} \wedge \alpha_2 = \alpha_{3} \wedge \bigwedge_\subbox{j \in J'_2 \cap J'_{3}} \beta_{2j} = \beta_{3j}} \implies\\ R_{12}\mpar{s'_1, s'_{2}}\psubst{\psi_1 \uplus \psi_2} \wedge R_{23}\mpar{s'_2, s'_{3}}\psubst{\psi_2 \uplus \psi_3}
-\end{multline*}
-Note that if  $R_{12}\mpar{s_1, s_2}$ or $ \mpar{R_{23}\mpar{s_2, s_3}}$ is false the statement trivially holds.
+\bigsymb{\bigexists} 
+\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X}, \bigsymb{\bigexists} 
+\mpar{t_{2x} = \OTx{2}{y}{2y}{2y} \in \fOT{s_2}}^{y \in Y},\\
+ V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1} \uplus \fvars{t_2} \uplus \fvars{t_3} \uplus \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \biguplus_{y\in Y}\fvars{t_{2y}}   \vdash \hspace{6cm}\\  \mpar{R_{12}\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2} \wedge \mpar{ R_{23}\mpar{s_2, s_3} \wedge 	g_2 \wedge g_3 \wedge \alpha_2 = \alpha_3 }
+%\wedge \bigwedge_\subbox{j \in J'_2 \cap J'_3} \beta_{2j} = \beta_{3j}} 
+%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} 
+\implies \hspace{6cm}\\
+%\exists
+%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
+\bigsymb{\bigwedge_{x\in X}}
+\mpar{
+\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_2 \land \bigwedge_\subbox{j \in J'_2 } \beta_{2j} = \beta_{1xj}\land g_{1 x}\land
+ R_{12}\mpar{s'_{1 x}, s'_2}\psubst{\psi_{1 x} \uplus \psi_2}} \wedge\\
+\bigsymb{\bigwedge_{y\in Y}}
+\mpar{
+\alpha_2=\alpha_{2 y}  \land J'_{2y}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{2yj}\land g_{1 y}\land
+ R_{23}\mpar{s'_{2 y}, s'_3}\psubst{\psi_{2 y} \uplus \psi_3}}\\
+\end{multline*}
+
+Note that if  either $R_{12}\mpar{s_1, s_2}$ or $R_{23}\mpar{s_2, s_3}$ is false the statement trivially holds.
 
@@
 \fOT{s_1} \times\fOT{s_2} \times \fOT{s_3}$\\
-\begin{multline*}
-V_1\uplus V_2 \uplus V_3 \uplus \fvars{t_1} \uplus \fvars{t_2} \uplus \fvars{t_3} \vdash \underbrace{R_{12}\mpar{s_1, s_2} \wedge  R_{23}\mpar{s_2, s_3}}_{R_{13}\mpar{s_1, s_3}} \wedge \\ g_1  \wedge g_{3}
-\wedge \alpha_1 = \alpha_{3}  \wedge \bigwedge_\subbox{j \in J'_1\cap J'_2 \cap J'_{3}} \beta_{1j} = \beta_{3j}
- \implies \underbrace{R_{12}\mpar{s'_1, s'_{2}}\wedge R_{23}\mpar{s'_2, s'_{3}}}_{R_{13}\mpar{s'_1, s'_3}} \psubst{\psi_1 \uplus \psi_2\uplus \psi_3 } 
-\end{multline*}
+
+\TODO{Manque Argument de simplification mecanique a trouver}
 By removing the variables of $A_2$ that have not effect on   $A_1$ et  $A_3$, we get the desired result.
@@
 
-Consider one $t_{1x}=\OT{s_1}{s_{1x}}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x}}}{g_{1x}}{\psi_{1x}}\in \fOT{s_1}$ to obtain a new open transition of A1 and compose it with $t_3^2$.
+Consider one $t_{1x}=\OT{s_1}{s_{1x}}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x}}}{g_{1x}}{\psi_{1x}}\in \fOT{s_1}$ to obtain a new open transition of $A_1$ and compose it with $t_3^2$.
 We obtain 
@@
 This specifies the family $\mpar{t_{13x}'}^{x\in X}$
-that allows us to prove the initial goal, i.e. the relation is preserved along identical transitions. We derive from the property ($\star$) and from the definition of $t_{13x}'$ and $t_{23}$
+that allows us to prove the initial goal, i.e. the relation is preserved along identical transitions. We derive  from the definition of  $t_{23}$
 \begin{multline*}
@@
 \implies \\
- R\mpar{s_{1}, s_{2}} \wedge 	g_{1} \wedge g_2 \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} \wedge \alpha_{1} = \alpha_{2} \bigwedge_\subbox{v_3\in V_3}
+ R\mpar{s_{1}, s_{2}} \wedge 	g_{1} \wedge g_2 \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} \wedge \alpha_{1} = \alpha_{2} \wedge \bigwedge_\subbox{v_3\in V_3}
  v^1_3=v^2_3\wedge s^1_3 = s^2_3
 \end{multline*}
-
+Furthermore, from the property ($\star$) and from the definition of $t_{13x}'$:
 \begin{multline*}
@@
 \bigwedge_{x\in X}
-\big(
- \alpha_{13}=\alpha_1=\alpha_{1 x}  \land J'_{1x}\uplus J'_3= J'_2\uplus J'_3\\
- \land \bigwedge_\subbox{j \in J'_2 \setminus\{k\} } \beta_{2j} = \beta_{1xj}
- \land \bigwedge_\subbox{j \in {j \in J^{2 \prime}_3} }  (\beta^2_{3j}) = (\beta^2_{3j}) \land g_{1 x}\land
- R'\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 x} \uplus \psi_2}\big)
-\wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} = \beta_{1xk}
-\end{multline*}
-Finally , because $R'\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 x} \uplus \psi_2} \implies R\mpar{s'_{1 3x}, s'_{23}}\psubst{(\psi_{1 x} \uplus \psi^2_3) \uplus (\psi_2 \uplus \psi^2_3)}$
+\Big(
+ \alpha_{13}=\alpha_1=\alpha_{1 x}  \land J'_{1x}\uplus J'_3= J'_2\uplus J'_3\land \\
+  \bigwedge_\subbox{j \in J'_2 \setminus\{k\} } \beta_{2j} = \beta_{1xj}
+ \land \bigwedge_\subbox{j \in {j \in J^{2 \prime}_3} }  (\beta^1_{3j}) = (\beta^2_{3j}) \land g_{1 x}\land
+ R\mpar{s'_{1x}, s'_{2}}\psubst{\psi_{1 x} \uplus \psi_2}\Big) \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} = \beta_{1xk}\\
+ \wedge \bigwedge_\subbox{v_3\in V_3}
+ v^1_3=v^2_3\wedge s^1_3 = s^2_3
+ \end{multline*}
+ \TODO{to check $j \in J'_2 \setminus\{k\}$}
+
+Finally, because $R'\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 x} \uplus \psi_2} \implies R'\mpar{s'_{1 3x}, s'_{23}}\psubst{(\psi_{1 x} \uplus \psi^2_3) \uplus (\psi_2 \uplus \psi^2_3)}$
 \begin{multline*}
@@
 $t_{23}$ is obtained  by  the transition $t_2=\OTx{2}{}{2}{2}$ alone with the state $s^2_3$ unchanged, if $k \not\in J_2'$
-\[t_{23} = \OT{\mpar{s_2, s^2_3}}{\mpar{s'_2, s^2_3}}{\alpha_2}{\beta_{2j}^{j \in J'_2}}{g_1}{\psi_2}
+\[t_{23} = \OT{\mpar{s_2, s^2_3}}{\mpar{s'_2, s^2_3}}{\alpha_2}{\beta_{2j}^{j \in J'_2}}{g_2}{\psi_2}
 \]
------------------------------\\
 As in the previous case, two cases are possible for $t_{13}$: either the hole $k$ of $A_1$ is involved in the transition or not.
@@
 
-In both cases note that $g_{13} \implies g_1$, with  $\mpar{s_1, s_2} \in S_1 \times S_2$, Definition~\ref{def:preservation} applied to OTs $t_1,\,t_2$ gives the following property that we denote ($\star$):
+In both cases note that $g_{13} \implies g_1$, with  $\mpar{s_1, s_2} \in S_1 \times S_2$, Definition~\ref{def:preservation} applied to OTs $t_1$ and $t_2$ gives the following property that we denote ($\star$):
 
@@
 We obtain 
-
 \[t_{13x}=\OT{(s_1,s^2_3)}{(s_{1x},s^2_3)}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x}}}{g_{1x}}{\psi_{1x}}\]
+In the same way this specifies the family, $\mpar{t_{13x}'}^{x\in X}$
+that allows us to prove the initial goal, i.e. the relation is preserved along identical transitions. We derive  from the definition of  $t_{23}$
+\begin{multline*}
+  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
+\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
+\implies \hspace{5cm}\\
+ R\mpar{s_{1}, s_{2}} \wedge 	g_{1} \wedge g_2  \wedge \alpha_{1} = \alpha_{2} \wedge \bigwedge_\subbox{v_3\in V_3}
+ v^1_3=v^2_3\wedge s^1_3 = s^2_3
+\end{multline*}
+
+And from the property ($\star$) and from the definition of $t_{13x}'$:
+\begin{multline*}
+  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
+\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
+\implies 
+\bigwedge_{x\in X}
+\Big(
+ \alpha_{13}=\alpha_1=\alpha_{1 x}  \land J'_{1x}\uplus J'_3= J'_2\uplus J'_3\land \\
+  \bigwedge_\subbox{j \in J'_2  } \beta_{2j} = \beta_{1xj}
+ \land \bigwedge_\subbox{j \in {j \in J^{2 \prime}_3} }  (\beta^1_{3j}) = (\beta^2_{3j}) \land g_{1 x}\land
+ R\mpar{s'_{1x}, s'_{2}}\psubst{\psi_{1 x} \uplus \psi_2}\Big) 
+ \wedge \bigwedge_\subbox{v_3\in V_3}
+ v^1_3=v^2_3\wedge s^1_3 = s^2_3
+ \end{multline*}
+
+The proof continues as described above.
 
@@
 \[t_{13x} = \left(\OT{\mpar{s^2_1, s_3}}{\mpar{{s^2_1}', s_{3}}}{\alpha_1^2}{ {(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{g^2_1}{\psi^2_1} \right)^{x\in X}\]
-\end{enumerate}
+
 We have to  prove the following formula in both cases (depending on how the transition $t_{12}$ is built): $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$ and
@@
 
-\item It remains to prove the  satisfaction of the  deadlock reducing condition:  for all $\mpar{s_{12}, s_{13}} \in S_{12} \times S_{13}$
+\item   It remains to prove the  satisfaction of the relation is preserved along identical transitions, i.e.
+the following is satisfied (we define $V_{12} = V_1 \uplus V_2$ and $ V_{23} = V_2\uplus V_3$):
+\begin{multline*}
+\forall \mpar{s_{12}, s_{13}} \in S_{12} \times S_{13}, \bigsymb{\forall} \mpar{t_{12}, t_{13}} = \mpar{\OTx{12}{}{12}{12}, \OTx{13}{}{13}{13}} \in \fOT{s_{12}} \times \fOT{s_{13}} \\ 
+\bigsymb{\bigexists} 
+\mpar{t_{12x} = \OTx{12}{x}{12x}{12x} \in \fOT{s_{12}}}^{x \in X},\\
+ V_{12} \uplus V_{13} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{12}} \uplus \fvars{t_{13}} 
+\vdash \hspace{6cm}\\  R\mpar{s_{12}, s_{13}} \wedge 	g_{12} \wedge g_{13} \wedge \alpha_{12} = \alpha_{13} 
+\implies \\
+\bigsymb{\bigwedge_{x\in X}}
+\mpar{
+ \alpha_{12}=\alpha_{12x} \land
+J'_{12x}  = J'_{13}  \land \bigwedge_\subbox{j \in  J'_{13}} \beta_{13j} = \beta_{12xj}\land g_{12x} \land
+ R\mpar{s'_{12x}, s'_{13}}\psubst{\psi_{12x} \uplus \psi_{13}}}
+\end{multline*}
+
+-----------------------------------------------------
+
+for all $\mpar{s_{12}, s_{13}} \in S_{12} \times S_{13}$
 \begin{multline*}
@@
 ~\qed
-%\end{enumerate}
+
+ \end{enumerate}
 

### 2022-06-22 2021-Refinement/paper/refinementarticle.tex
proof thm1, thm2 and debut thm3

@@
 \begin{multline*}
-\forall \mpar{s_1, s_3} \in S_1 \times S_3, \bigsymb{\forall} \mpar{t_1, t_3} = \mpar{\OTx{1}{}{1}{1}, \OTx{3}{}{3}{3}} \in \fOT{s_1} \times \fOT{s_3} \\ 
+\bigforall \mpar{s_1, s_3} \in S_1 \times S_3, \bigsymb{\forall} \mpar{t_1, t_3} = \mpar{\OTx{1}{}{1}{1}, \OTx{3}{}{3}{3}} \in \fOT{s_1} \times \fOT{s_3} \\ 
 \bigsymb{\bigexists} 
@@
 \end{multline*}
-According to the refinement relation between  $A_1$ and $A_2$ we have:
-\begin{multline*}
-\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_2} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\ 
+Firstly, according to the refinement relation between  $A_1$ and $A_2$ we have:
+\begin{multline*}
+\bigforall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_2} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\ 
 \bigsymb{\bigexists} 
@@
 \begin{multline*}
-\forall \mpar{s_2, s_3} \in S_1 \times S_3, \bigsymb{\forall} \mpar{t_2, t_3} = \mpar{\OTx{2}{}{2}{2}, \OTx{3}{}{3}{3}} \in \fOT{s_2} \times \fOT{s_3} \\ 
+\bigforall \mpar{s_2, s_3} \in S_1 \times S_3, \bigsymb{\forall} \mpar{t_2, t_3} = \mpar{\OTx{2}{}{2}{2}, \OTx{3}{}{3}{3}} \in \fOT{s_2} \times \fOT{s_3} \\ 
 \bigsymb{\bigexists} 
@@
 \mpar{
-\alpha_2=\alpha_{2 x}  \land J'_{2x}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{2xj}\land g_{1 x}\land
+\alpha_2=\alpha_{2 x}  \land J'_{2x}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{2xj}\land g_{2 x}\land
  R_{23}\mpar{s'_{2 x}, s'_3}\psubst{\psi_{2 x} \uplus \psi_3}}\\
@@
 
-For each $s_2 \in S_2$, we remark that  $s_2$  allows to relate $s_1$ and $s_3$ if and only if $R_{12}\mpar{s_1, s_2}\land R_{23}\mpar{s_2, s_3} $. 
-We can make the conjunction of these two formulas,
-we get  $\forall \mpar{s_1,s_2,s_3} \in S_1\times S_2 \times S_3$ and\\ $\bigsymb{\forall} \mpar{t_1,t_2, t_{3}}\!=\!
-\mpar{\OTx{1}{}{1}{1},\OTx{2}{}{2}{2},\OTx{3}{}{3}{3}}\!
-\in\!
-\fOT{s_1} \times\fOT{s_2} \times \fOT{s_3}$
+Note that if  either $R_{12}\mpar{s_1, s_2}$ or $R_{23}\mpar{s_2, s_3}$ is false the statement trivially holds.
+So for each $s_2 \in S_2$, we remark that  $s_2$  allows to relate $s_1$ and $s_3$ if and only if $R_{12}\mpar{s_1, s_2}\land R_{23}\mpar{s_2, s_3} $.
+We pick a state $s_2$ relating both,  we can then the following be inferred from the above formulas:
+$\forall \mpar{s_1,s_3} \in S_1 \times S_3$ and\\ $\bigsymb{\forall} \mpar{t_1, t_{3}}\!=\! \mpar{\OTx{1}{}{1}{1},\OTx{3}{}{3}{3}}\! \in\! \fOT{s_1} \times \fOT{s_3}$  
 \begin{multline*}
 \bigsymb{\bigexists} 
-\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X}, \bigsymb{\bigexists} 
-\mpar{t_{2x} = \OTx{2}{y}{2y}{2y} \in \fOT{s_2}}^{y \in Y},\\
- V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1} \uplus \fvars{t_2} \uplus \fvars{t_3} \uplus \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \biguplus_{y\in Y}\fvars{t_{2y}}   \vdash \hspace{6cm}\\  \mpar{R_{12}\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2} \wedge \mpar{ R_{23}\mpar{s_2, s_3} \wedge 	g_2 \wedge g_3 \wedge \alpha_2 = \alpha_3 }
+\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},\\
+ V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1} \uplus \fvars{t_2} \uplus \fvars{t_3} \uplus \biguplus_{x\in X}\fvars{t_{1x}}     \vdash \hspace{6cm}\\  R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \wedge 	g_1 \wedge g_2 \wedge   g_3\wedge  \alpha_1 = \alpha_2  \wedge \alpha_2 = \alpha_3
 %\wedge \bigwedge_\subbox{j \in J'_2 \cap J'_3} \beta_{2j} = \beta_{3j}} 
@@
 \alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_2 \land \bigwedge_\subbox{j \in J'_2 } \beta_{2j} = \beta_{1xj}\land g_{1 x}\land
- R_{12}\mpar{s'_{1 x}, s'_2}\psubst{\psi_{1 x} \uplus \psi_2}} \wedge\\
-\bigsymb{\bigwedge_{y\in Y}}
-\mpar{
-\alpha_2=\alpha_{2 y}  \land J'_{2y}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{2yj}\land g_{1 y}\land
- R_{23}\mpar{s'_{2 y}, s'_3}\psubst{\psi_{2 y} \uplus \psi_3}}\\
-\end{multline*}
-
-Note that if  either $R_{12}\mpar{s_1, s_2}$ or $R_{23}\mpar{s_2, s_3}$ is false the statement trivially holds.
-
-By rearranging and simplifying we get:$\forall \mpar{s_1,s_2,s_3} \in S_1\times S_2 \times S_3$, $ \bigsymb{\forall} \mpar{t_1,t_2, t_{3}}\!=\!
-\\\mpar{\OTx{1}{}{1}{1},\OTx{2}{}{2}{2},\OTx{3}{}{3}{3}}\!
-\in\!
-\fOT{s_1} \times\fOT{s_2} \times \fOT{s_3}$\\
-
-\TODO{Manque Argument de simplification mecanique a trouver}
-By removing the variables of $A_2$ that have not effect on   $A_1$ et  $A_3$, we get the desired result.
+ R_{12}\mpar{s'_{1 x}, s'_2}\psubst{\psi_{1 x} \uplus \psi_2}} \wedge\\ R_{23}\mpar{s'_{2}, s'_3}\psubst{\psi_{2} \uplus \psi_3}\hspace{6cm}\\
+\end{multline*}
+By rearranging, simplifying and removing the variables of $A_2$ that have not effect on   $A_1$ et  $A_3$, we get the desired result.
 
@@
 \begin{multline*}
-\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}, \bigsymb{\forall} \mpar{t_{13}, t_{23}} = \mpar{\OTx{13}{}{13}{13}, \OTx{23}{}{23}{23}} \in \fOT{s_{13}} \times \fOT{s_{23}} \\ 
+\bigforall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}, \bigsymb{\forall} \mpar{t_{13}, t_{23}} = \mpar{\OTx{13}{}{13}{13}, \OTx{23}{}{23}{23}} \in \fOT{s_{13}} \times \fOT{s_{23}} \\ 
 \bigsymb{\bigexists} 
@@
 We pick $s_{13}$, $s'_{13a}$, and two open transitions $t_{13}$ and $t_{23}$.
-Where $s_{13}=(s_1,s_3)$ and $s_{23}=(s_2,s_3)$ by construction of $R$.
+Where $s_{13}=(s_1,s_3)$ and $s_{23}=(s_2,s_3)$ by construction of $R'$.
 
@@
 
-$\bullet$ if  the hole $k$ of A1 is not involved in the transition:
+$\bullet$ if  the hole $k$ of $A_1$ is not involved in the transition:
 $t_1=\OTx{1}{}{1}{1}$ when  $k \not\in J'_{1} $
@@
 
-Consider one $t_{1x}=\OT{s_1}{s_{1x}}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x}}}{g_{1x}}{\psi_{1x}}\in \fOT{s_1}$ to obtain a new open transition of $A_1$ and compose it with $t_3^2$.
+Consider one $t_{1x}=\OT{s_1}{s_{1x}}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x}}}{g_{1x}}{\psi_{1x}}\in \fOT{s_1}$ to obtain a new open transition of $A_{13}$ and compose it with $t_3^2$.
 We obtain 
@@
  \end{multline*}
- \TODO{to check $j \in J'_2 \setminus\{k\}$}
+ \TODO{to check why $j \in J'_2 \setminus\{k\}$}
 
@@
  V_{12} \uplus V_{13} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{12}} \uplus \fvars{t_{13}} 
-\vdash \hspace{6cm}\\  R\mpar{s_{12}, s_{13}} \wedge 	g_{12} \wedge g_{13} \wedge \alpha_{12} = \alpha_{13} 
+\vdash \hspace{6cm}\\  R'\mpar{s_{12}, s_{13}} \wedge 	g_{12} \wedge g_{13} \wedge \alpha_{12} = \alpha_{13} 
 \implies \\
@@
 J'_{12x}  = J'_{13}  \land \bigwedge_\subbox{j \in  J'_{13}} \beta_{13j} = \beta_{12xj}\land g_{12x} \land
- R\mpar{s'_{12x}, s'_{13}}\psubst{\psi_{12x} \uplus \psi_{13}}}
-\end{multline*}
-
------------------------------------------------------
+ R'\mpar{s'_{12x}, s'_{13}}\psubst{\psi_{12x} \uplus \psi_{13}}}
+\end{multline*}
+
+We pick $s_{12}$, $s'_{12a}$, and two open transitions $t_{12}$ and $t_{13}$.
+Where $s_{12}=(s_1,s_2)$ and $s_{13}=(s_1,s_3)$ by construction of $R'$.
+
+We reason on the way the OT $t_{13}$ has been obtained: either the hole $k$ of $A_1$ is involved in the transition or not.
+
+\paragraph{First case: Both $A_1$ and $A_3$ are involved in transition $t_{13}$.}
+The transition $t_{13}$  is obtained  by the composition of transitions $t_3=\OTx{3}{}{3}{3}$ and  \[t_1^1=
+\OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{   {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1} \qquad \text{ when } k \in {J^1_{1}}^{\prime}
+\]
+The result is the transition:
+\[
+t_{13} = \OT{\mpar{s^1_1, s_3}}{\mpar{{s^1_1}',s'_3 }}{\alpha^1_1}{{\beta^1_{1j}}^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {(\beta_{3j})^{j \in J^{\prime}_3} }}{g^1_1 \wedge g_3 \wedge \alpha_3 = \beta^1_{1k}}{\psi^1_1 \uplus \psi_3} \qquad \text{ where } k \in {J^1_{1}}^{\prime}
+\]
+
+According to the refinement relation between  $A_2$ and $A_3$ we have the following property that we denote $(*)$:
+\begin{multline*}
+\bigforall \mpar{s_2, s_3} \in S_1 \times S_3, \bigsymb{\forall} \mpar{t_2, t_3} = \mpar{\OTx{2}{}{2}{2}, \OTx{3}{}{3}{3}} \in \fOT{s_2} \times \fOT{s_3} \\ 
+\bigsymb{\bigexists} 
+\mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X},
+V_2 \uplus V_3\uplus \biguplus_{x\in X}\fvars{t_{2x}} \uplus \fvars{t_3} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R_{23}\mpar{s_2, s_3} \wedge 	g_2 \wedge g_3 \wedge \alpha_2 = \alpha_3 
+%\wedge \bigwedge_\subbox{j \in J'_2 \cap J'_3} \beta_{2j} = \beta_{3j} 
+\implies \hspace{6cm}\\
+%\exists
+%\OTx{1}{a}{3}{3}\in \fOT{s_2}. \\
+\bigsymb{\bigwedge_{x\in X}}
+\mpar{
+\alpha_2=\alpha_{2 x}  \land J'_{2x}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{2xj}\land g_{2 x}\land
+ R\mpar{s'_{2 x}, s'_3}\psubst{\psi_{2 x} \uplus \psi_3}}\\
+\end{multline*}
+From the
+
+Consider any transition $t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}$ and compose it with  $t^1_1$. We get a family of  transitions:
+\[
+t_{12x}^{x\in X} = \mpar{\OT{\mpar{s^1_1, s_{2x}}}{\mpar{{s^1_1}',s'_{2x} }}{\alpha^1_1}{{\beta^1_{1j}}^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {(\beta_{2xj})^{j \in J^{\prime}_{2x}} }}{g^1_1 \wedge g_{2x} \wedge \alpha_{2x} = \beta^1_{1k}}{\psi^1_1 \uplus \psi_{2x}}}^{x\in X}  \quad \text{where } k \in {J^1_{1}}^{\prime}
+\]
+In order to prove the goal of of the expected relation let us start with the hypothesis:
+\begin{multline*}
+V_{12} \uplus V_{13} \uplus  \biguplus_{x\in X}\fvars{t_{2x}}  \uplus \fvars{t_{12}} \uplus \fvars{t_{13}} 
+\vdash \hspace{6cm}\\  R'\mpar{s_{12}, s_{13}} \wedge 	g_{12} \wedge g_{13} \wedge \alpha_{12} = \alpha_{13} 
+\implies  R\mpar{s_{2}, s_{3}}\wedge \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1 \wedge s^1_1 = s^2_1 \wedge \\
+g_1\wedge g^1_1 \wedge g_3 \wedge \alpha_3 = \beta^1_{1k} \wedge \alpha_2 = \alpha_3
+\end{multline*}
+From the property $(*)$ we get:
+
+\newpage
 

### 2022-06-27 2021-Refinement/paper/refinementarticle.tex
proof meeting notes

@@
  \land \bigwedge_\subbox{j \in {j \in J^{2 \prime}_3} }  (\beta^1_{3j}) = (\beta^2_{3j}) \land g_{1 x}\land
- R\mpar{s'_{1x}, s'_{2}}\psubst{\psi_{1 x} \uplus \psi_2}\Big) \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} = \beta_{1xk}\\
+ R\mpar{s'_{1x}, s'_{2}}\psubst{\psi_{1 x} \uplus \psi_2}\wedge \alpha^2_3 = \beta_{2k} = \beta_{1xk}\Big) \wedge g^2_3 \\
  \wedge \bigwedge_\subbox{v_3\in V_3}
@@
  \end{multline*}
- \TODO{to check why $j \in J'_2 \setminus\{k\}$}
 
@@
 
-The proof continues as described above.
-
--------------------------------\\
-
-\TODO{NEW PROOF SKETCH}
-HYPOTHESES and OBJECTIVES
-
-TWO cases for the OT $t_{23}$
-
-CASE 1 : $k$ does not move in $A_2$
-
-two cases for  $t_{13}$
-
- ...
-
-in both cases relation is preserved along identical transitions applied on A1 vs A2 provides a $t_{1}'$ such that HOLE $k$ does not move
-
-and has the desired property for ``relation is preserved along identical transitions''
-
-CASE 2 : k moves in $A_2$ with action $\beta_{2 k}$, and $A_3$ does the labelled action $\beta_{2 k}$.
-
-two cases for  $t_{13}$
-
- ...
-
-in both cases relation is preserved along identical transitions applied on A1 vs A2 provides a $t_{1}'$ such that HOLE $k$ should move with the action $\beta_{2 k}$.
-
-We recompose a $t_{1}'$ with $t_{1}'$ and $t_3$ from  $t_{23}$
-
-it has the desired property for ``relation is preserved along identical transitions''
-
-relation on guards should hold but to be formulated carefully.
-
-\TODO{END OF NEW PROOF SKETCH}
+The proof continues as described above. \TODO{finish the proof}
+
 \begin{comment}

### 2022-06-29 2021-Refinement/paper/refinementarticle.tex
end of proof
Abstract V2

@@
 \begin{abstract}
-\TODO{ The abstract should briefly summarize the contents of the paper in 150--250 words.}
+%\TODO{ The abstract should briefly summarize the contents of the paper in 150--250 words.}
 
 Establishing equivalences and refinement relations between programs is an important mean for 
-verifying the correctness of programs, by formally proving the relation between a specification and an implementation, 
-proving that two implementation are equivalent, or justifying optimisations and transformations, by establishing that the
-behaviours of a modified program simulate those of to the source one.
-
-In this article, we discuss a notion of refinement between so-called "open automata", which are symbolic
-behavioural models for communicating systems. Open automata may have "holes" modelling elements of their
+verifying the correctness of programs. By establishing that the
+behaviours of a modified program simulate those of to the source one, simulaiton and bisimulation relations  formalise the desired  relation between a specification and an implementation, 
+ two equivalent implementations, or a program and its optimised implementation.
+This article discusses a notion of refinement between \emph{open automata}, which are symbolic
+behavioural models for communicating systems. 
+Open automata may have \emph{holes} modelling elements of their
 context, and can be composed by instantiation of the holes. This allows for a compositional approach for
-verification of their behaviour, essential to address proofs about large realistic systems.
+verification of their behaviour.
 
 We define several variants of refinement between systems including either equal or different sets of holes, and 
-show under which conditions these refinements are preserved by composition of open automata. We also discuss
-the relations between these refinements and the existence of deadlocks.
-We illustrate these notions on several simple use-cases.
+show under which conditions these refinements are preserved by composition of open automata.
 
@@
 
-The proof continues as described above. \TODO{finish the proof}
+%The proof continues as described above. \TODO{finish the proof}
+
+Which gives directly $R'\mpar{s'_{1 3x}, s'_{23}}$ as $A_3$ does not move (thus $\psi_{1 3x}=\psi_{1 x}$ and  $\psi_{23} =\psi_{2}$):
+\begin{multline*}
+  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
+\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
+\implies \\
+\bigwedge_{x\in X}
+\mpar{
+ \alpha_{13}=\alpha_{1 3x} \land
+J'_{13x}  = J'_{23}  \land \bigwedge_\subbox{j \in  J'_{23}} \beta_{23j} = \beta_{13xj}\land g_{1 3x} \land
+ R'\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 3x} \uplus \psi_{23}}}
+\end{multline*}
+
+This concludes for the second case.
 

### 2022-06-30 2021-Refinement/paper/refinementarticle.tex
Introductino -- V0.1

@@
 \section{Introduction}
-\TODO{1.5 pages}
-
-Contributions:
-
-We first: introduce open automata (NOT NEW), their composition, 
-and the deadlock-free composition.
-
+
+Automata are convenient for specifying and verifying systems, but most automata definitions allow only the specifications of finite closed systems.
+Indeed those systems are the ones we can veify efficiently, but programming often consist in writing open systems that should be interfaced with others, and with potentially unbound behaviours (at least statically).We investigate in our works the possibility to define open symbolic systems, verify some of their properties, and use them to compose in a structured way more complex systems.
+
+Refinement relations verify that and implementation satisfies some properties with respect to a specification.
+Refinement entails that one system can be considered as a more precise version of the specification, featuring all the specified behaviours with more concrete details.
+In this article we mostly rely on a simulation point of view, where all the specified behaviour must be followed by the refined system but additionla behaviours may exist.
+However we also ensure that a while scenario, made of several steps, of the specification can also be simulated by the refined system, which is a bit richer than the traditional simulation relation.
+
+Open automata were defined as a way to provide a semantics for open parameterized hierarchical LTSs used in verification tools.
+An open automaton \cite{henrio:01299562} is a classical automaton with variables and holes.
+Variables makes autoomata symbolic and allow them to encode infinite state systems.
+Holes enables the composition of automata: an automaton with a hole is an operator that takes another automaton as parameter and reacts to the actions it emits; the composed automaton is a more precise automaton where the behaviour of one ``parameter'' of the main automaton has been provided.
+
+In previous works \cite{2007.10770,wang:03126313} a bisimulation relation was defined for open automata and open parameterized hierarchical LTSs.
+It has already good properties relatively to bisimulation, but refinement relations were not studied.
+
+This article first introduces open automata that were defined in  \cite{henrio:01299562},  but compared to previous works, we additionally define the composition of open automata.
 Then we define  a refinement relation for open automata that has the following characteristics:
-
-- good behaviour wrt composition
-
-- refinement does not introduce deadlock
-
-- a first relation that focuses on the automaton part 
-and a second that deals with open behaviour
-
-we will see that having at the same time composition and transitivity also raises challenges; we introduce a new form of refinement relation that addresses this challenge.
+\begin{itemize}
+\item Classical simulation characterisation but also an additional criteria ensuring that refinement does not introduce deadlocks when following a trace from the simulated automaton.
+\item Good properties relatively to composition: we prove here that filling the same hole  with the same automaton preserves the refinement relation.
+\item Ability to take into account both composition and transitivity: this is a challenge because composition changes the set of holes of the open automaton and refinement takes into account actions of the holes.
+\end{itemize}
+The refinement relation is introduced in two steps.
+First we define a refinement that relates two automata with the same holes, which allows us to focus on the automaton aspect.
+Second we introduce a relation that relates two automata with different sets of holes, which allows us to take into account the open nature of open automata, and to deal with composition.
 

### 2022-06-30 2021-Refinement/paper/refinementarticle.tex
Plan

@@
 
+The following of this article is organised as follows. 
+We first review related works in Section~\ref{sec:sota}; then Section~\ref{sec:background} recalls the definition of open automata and defines their composition. 
+We  then  define a refinement relation for open automata, first only considering two automata with the same set of holes in Section~\ref{sec:refinement} and generalize it to automataa with a different set of holes in Section~\ref{sec:holes} before proving basic properties of refinement in Section~\ref{sec:prop}; here we prove that refinement is a preorder and we focus on one composition property.
+Section~\ref{sec:ccl} concludes the paper.
+
 \section{Related Work}
@@
 
-\section{a recuperer si on se rend compte que c'est utile}
-When we will introduce refinements in Section \ref{sec:prelref}, setting an undefined variable will be considered a valid refinement, for instance a \(5\) bits register is a particular \(n\) bits register.
+%\section{a recuperer si on se rend compte que c'est utile}
+%When we will introduce refinements in Section \ref{sec:prelref}, setting an undefined variable will be considered a valid refinement, for instance a \(5\) bits register is a particular \(n\) bits register.
 

### 2022-06-30 2021-Refinement/paper/refinementarticle.tex
A conclusion

@@
 
-The notion of refinement aims captures the relation between  a specification and an implementation of the same component.
+The notion of refinement  captures the relation between  a specification and an implementation of the same component.
 It is usually defined as trace inclusion or simulation \cite{Milner:1980, Kouchnarenko:2007}; this ensures that all behaviours of the implementation must be also behaviours of the specification.
@@
 
+\TODO{The refinement relation  also specifies that the refined process must follow the behaviour of the specification, not only at every compatible state but also along any trace.}
+
  We will show in Section~\ref{sec:prop} that this refinement relation has good properties in terms of transitivity, compositionality, reflexivity, etc.
@@
 
-Open automata compositionis a refinement where
+Open automata composition is a refinement where
 the tracked holes are the holes of the base automaton minus the composed hole.
@@
 \section{Conclusion}\label{sec:ccl}
-\TODO{0.5 pages}
+In this article we investigated the notion of refinement for a symbolic and open model: open automata. 
+Open automata are convenient to model parallel systems that are parameterised both by the use of variables and by the possibility to compose automata.
+The refinement relation first relies on a simulation relation between the specification and its refinement, but it also specifies that the refined process must follow the behaviour of the specification, not only at every compatible state but also along any trace.
+We finally showed that refinement is a preorder that is preserved when filling a hole.
+
+In the future we will focus on the other composition property that considers the preservation of refinement when automata are placed in the same context, namely filling the hole of the same automaton by an automaton and its refinement.
+This property should require some restriction on the composed processes.
+ Finally, we will investigate under which condition, the composition operation produces a refinement in the sense that filling a hole produces a refined process.
 

### 2022-06-30 2021-Refinement/paper/refinementarticle.tex
ajout figure + Defintion 4

--- 2022-06-30 2021-Refinement/paper/refinementarticle.tex
@@
 \section{Introduction}
-
-Automata are convenient for specifying and verifying systems, but most automata definitions allow only the specifications of finite closed systems.
-Indeed those systems are the ones we can veify efficiently, but programming often consist in writing open systems that should be interfaced with others, and with potentially unbound behaviours (at least statically).We investigate in our works the possibility to define open symbolic systems, verify some of their properties, and use them to compose in a structured way more complex systems.
-
-Refinement relations verify that and implementation satisfies some properties with respect to a specification.
-Refinement entails that one system can be considered as a more precise version of the specification, featuring all the specified behaviours with more concrete details.
-In this article we mostly rely on a simulation point of view, where all the specified behaviour must be followed by the refined system but additionla behaviours may exist.
-However we also ensure that a while scenario, made of several steps, of the specification can also be simulated by the refined system, which is a bit richer than the traditional simulation relation.
-
-Open automata were defined as a way to provide a semantics for open parameterized hierarchical LTSs used in verification tools.
-An open automaton \cite{henrio:01299562} is a classical automaton with variables and holes.
-Variables makes autoomata symbolic and allow them to encode infinite state systems.
-Holes enables the composition of automata: an automaton with a hole is an operator that takes another automaton as parameter and reacts to the actions it emits; the composed automaton is a more precise automaton where the behaviour of one ``parameter'' of the main automaton has been provided.
-
-In previous works \cite{2007.10770,wang:03126313} a bisimulation relation was defined for open automata and open parameterized hierarchical LTSs.
-It has already good properties relatively to bisimulation, but refinement relations were not studied.
-
-This article first introduces open automata that were defined in  \cite{henrio:01299562},  but compared to previous works, we additionally define the composition of open automata.
+\TODO{1.5 pages}
+
+Contributions:
+
+We first: introduce open automata (NOT NEW), their composition, 
+and the deadlock-free composition.
+
 Then we define a refinement relation for open automata that has the following characteristics:
-\begin{itemize}
-\item Classical simulation characterisation but also an additional criteria ensuring that refinement does not introduce deadlocks when following a trace from the simulated automaton.
-\item Good properties relatively to composition: we prove here that filling the same hole  with the same automaton preserves the refinement relation.
-\item Ability to take into account both composition and transitivity: this is a challenge because composition changes the set of holes of the open automaton and refinement takes into account actions of the holes.
-\end{itemize}
-The refinement relation is introduced in two steps.
-First we define a refinement that relates two automata with the same holes, which allows us to focus on the automaton aspect.
-Second we introduce a relation that relates two automata with different sets of holes, which allows us to take into account the open nature of open automata, and to deal with composition.
+
+- good behaviour wrt composition
+
+- refinement does not introduce deadlock
+
+- a first relation that focuses on the automaton part 
+and a second that deals with open behaviour
+
+we will see that having at the same time composition and transitivity also raises challenges; we introduce a new form of refinement relation that addresses this challenge.
 
@@
 
+In Fig.
+\ref{Fig:SpecOA} we present a very simple example of an open automaton inspired from \cite{Gorrieri:2001}.
+An automaton that we name \texttt{database} modelling a data base that can be queried and updated.
+The open automaton \texttt{counter}    depicting  the behaviour of the timer is illustrated in Fig.
+\ref{Fig:counter}.
+
+\begin{figure}[h]
+ \centering
+   \includegraphics[width=.9\textwidth]{Figures/database.pdf}
+   \caption{Open Automaton. It exposes an unspecified counter in the hole
+ to count external tick actions. The system sets a counter when a query is enabled and updates  when  the time is over.\label{Fig:SpecOA}}
+\end{figure}
+
 \paragraph{Open automaton composition}
@@
 
-\TODO{peut etre echanger c et p? ou c devient p et p devient? }
 \begin{definition}[Composition of open automata] \label{Def:CompOA}
-The composition of \(A_c = \OAg[c]\) in the hole \(k \in J_p\) of \(A_p = \OAg[p]\) is the OA defined as follows:
-\[A_p\subst{A_c}{k} ::=  \OA{S_p \times S_c}{\mpar{s_{0p}, s_{0c}}}{V_p \uplus V_c}{\sigma_{0p} \uplus \sigma_{0c}}{J_c \uplus J_p \setminus \mbrc{k}}{T} \] \text{with }
-
-\begin{align*}
-T=& \mset{\OT{\mpar{s_p, s_c}}{\mpar{s'_p, s'_c}}{\alpha_p}{\beta_j^{j \in J'_c \uplus J'_p}}{g_p \wedge g_c \wedge \alpha_c = \beta_k}{\psi_p \uplus \psi_c}}{ \OT{s_p}{s'_p}{\alpha_p}{\beta_j^{j \in J'_p \uplus \mbrc{k} }}{g_p}{\psi_p} \in T_p, \OTx{c}{}{}{c} \in T_c} \\
-	& \cup \mset{\OT{\mpar{s_p, s_c}}{\mpar{s'_p, s_c}}{\alpha_p}{\beta_j^{j \in J'_p}}{g_p}{\psi_p}}{\OTx{p}{}{}{p} \in T_p, k \notin J'_p, s_c \in S_c}
+The composition of \(A_p = \OAg[p]\) in the hole \(k \in J_c\) of \(A_c = \OAg[c]\) is the OA defined as follows:
+\[A_c\subst{A_p}{k} ::=  \OA{S_c \times S_p}{\mpar{s_{0c}, s_{0p}}}{V_c \uplus V_p}{\sigma_{0c} \uplus \sigma_{0p}}{J_p \uplus J_c \setminus \mbrc{k}}{T} \] \text{with }
+
+\begin{align*}
+T=& \mset{\OT{\mpar{s_c, s_p}}{\mpar{s'_c, s'_p}}{\alpha_c}{\beta_j^{j \in J'_p \uplus J'_c}}{g_c \wedge g_p \wedge \alpha_p = \beta_k}{\psi_c \uplus \psi_p}}{ \OT{s_c}{s'_c}{\alpha_c}{\beta_j^{j \in J'_c \uplus \mbrc{k} }}{g_c}{\psi_c} \in T_c, \OTx{p}{}{}{p} \in T_p} \\
+	& \cup \mset{\OT{\mpar{s_c, s_p}}{\mpar{s'_c, s_p}}{\alpha_c}{\beta_j^{j \in J'_c}}{g_c}{\psi_c}}{\OTx{c}{}{}{c} \in T_c, k \notin J'_c, s_p \in S_p}
 \end{align*}
 \end{definition}
+
 The first OA decides when the second can evolve by involving its hole in a transition:
-The action emitted when \(A_c\) makes a transition is synchronised with the action of the hole \(k\) in transitions of \(A_p\) .
+The action emitted when \(A_p\) makes a transition is synchronised with the action of the hole \(k\) in transitions of \(A_c\).
+
+\begin{figure}[h]
+ \centering
+   \includegraphics[width=.5\textwidth]{Figures/counter.pdf}\hfill 
+   \includegraphics[width=.3\textwidth]{Figures/compose_count_db.pdf}
+   \caption{Open Automaton of \texttt{counter} process (left).
+Its role is to get a target, then count ticks until that target is reached, then emit an action with the elapsed time and restart.
+And Open Automation of  the composition \texttt{database}[\texttt{counter}] (right).\label{Fig:counter}}
+\end{figure}
 
@@
 A relation (bisimulation, refinement, etc.) between open automata requires to compare their states.
-To do so we will suppose that the variables of the two OAs are disjoint (a renaming of variables may have to be applied before comparing OA states)
+To do so we will suppose that the variables of the two OAs are disjoint (a renaming of variables may have to be applied before comparing OA states).
 \begin{definition}[Relation on OA states] Suppose $V_1$ and $V_2$ are disjoint.
@@
 With such a relation we are able to check the refinement between two open automata with the same level of abstraction but specified differently, for example, by duplicating states, removing transitions,  reinforcing  guards, modifying variables.
+
+To illustrate the refinement simulation of open automata, consider a variation on the \texttt{database} automaton of Fig.
+\ref{Fig:RefineOA}.
+We suppose that on more concrete level, in addition to querying and updating the data base,  a backup copy of it may also be made.
+
+\begin{figure}[h]
+ \centering
+   \includegraphics[width=.9\textwidth]{Figures/databaseRefine.pdf}
+   \caption{The refined Open Automaton of the automaton of Fig.\ref{Fig:SpecOA}.
+Two other actions,  in addition to  \texttt{qry} and \texttt{upd},  \texttt{back} representing a request to make a backup copy and    \texttt{cpy} is used to reflect the actual operation of copying.
+\label{Fig:RefineOA}}
+\end{figure}
 

### 2022-06-30 2021-Refinement/paper/refinementarticle.tex
minor change

@@
 \begin{definition}[Composition of open automata] \label{Def:CompOA}
-The composition of \(A_p = \OAg[p]\) in the hole \(k \in J_c\) of \(A_c = \OAg[c]\) is the OA defined as follows:
+The composition of \(A_c = \OAg[c]\) in the hole \(k \in J_c\) of  \(A_p = \OAg[p]\) is the OA defined as follows:
 \[A_c\subst{A_p}{k} ::=  \OA{S_c \times S_p}{\mpar{s_{0c}, s_{0p}}}{V_c \uplus V_p}{\sigma_{0c} \uplus \sigma_{0p}}{J_p \uplus J_c \setminus \mbrc{k}}{T} \] \text{with }

### 2022-07-01 2021-Refinement/paper/refinementarticle.tex
minor changes in intro RW and notations

@@
 
-Refinement relations verify that and implementation satisfies some properties with respect to a specification.
+The notion of refinement  captures the relation between  a specification and an implementation of the same component.
 Refinement entails that one system can be considered as a more precise version of the specification, featuring all the specified behaviours with more concrete details.
+ It is usually defined as trace inclusion or simulation  \cite{Milner:1980,Kouchnarenko:2007}; this ensures that all behaviours of the implementation must be also behaviours of the specification.
+ This definition, which is based on systems whose behaviour is fully defined, is not well-suited for open systems,  as it requires to reason also about unspecified behaviours.
 In this article we mostly rely on a simulation point of view, where all the specified behaviour must be followed by the refined system but additionla behaviours may exist.
@@
 
-In previous works \cite{2007.10770,wang:03126313} a bisimulation relation was defined for open automata and open parameterized hierarchical LTSs.
+In previous works \cite{fhbisim,wang:03126313} a bisimulation relation was defined for open automata and open parameterized hierarchical LTSs.
 It has already good properties relatively to bisimulation, but refinement relations were not studied.
@@
 \TODO{1 page}
-
-The notion of refinement  captures the relation between  a specification and an implementation of the same component.
-It is usually defined as trace inclusion or simulation \cite{Milner:1980, Kouchnarenko:2007}; this ensures that all behaviours of the implementation must be also behaviours of the specification.
-This definition, which is based on systems whose behaviour is fully defined, is not well-suited for open systems,  as it requires to reason also about unspecified behaviours.
+\TODO{move to the end?}
 
@@
 In an article by Hou, Zechen and Madelaine \cite{10.1145/3372884.3373161}, a computable bisimulation is introduced and proved equivalent to the previous bisimulation already introduced.
-In a more recent work by Ameur-Boulifa, Henrio and Madelaine \cite{2007.10770}, a weak version of the bisimulation on open automata is introduced.
+In a more recent work by Ameur-Boulifa, Henrio and Madelaine \cite{fhbisim}, a weak version of the bisimulation on open automata is introduced.
 These works differ from ours because the relation introduced in this report is a refinement relation in the form of a simulation and not a bisimulation.
@@
 
-\section{Background: Open Automata and their Composition}\label{sec:background}
-\TODO{3.5 pages}
+\section{Open Automata and their Composition}\label{sec:background}
 
@@
 
-Families of values, or equivalently maps will be noted \(\mset{i \mapsto x_i}{i \in I}\), \(\mset{i \gets x_i}{i \in I}\) or \(x_i^{i \in I}\).
+\subsection{Preliminaries and notations}
+Families of values, or equivalently maps will be noted \(\mset{i \mapsto x_i}{i \in I}\), or \(\mset{i \gets x_i}{i \in I}\), or \(x_i^{i \in I}\) depending on what is more convenient.
 % TODO: introduire le fait que \exists c_j^{j \in J} défini J et {j \mapsto c_j}
@@
 %For instance \(\mbrc{\alpha \mapsto 1, \beta \mapsto 2, \gamma \mapsto 3}\) has no simple generating expression and is better represented with the finite version of first notation.
-The disjoint union on set is noted \(\uplus\)\footnote{\(\uplus\) notation either supposes that the sets are disjoint or rename conflicting objects depending on the context}.
+The disjoint union on set is noted \(\uplus\).
+%\footnote{Depending on the context, \(\uplus\) notation either supposes that the sets are disjoint or constraints joined sets to be disjoints if several choices are possible}.
 Disjoint union is also used on maps.
-%There are several ways of ensuring a union is disjoint, we will indifferently either suppose sets are disjoint or rename conflicting object (useful for variables).
+There are several ways of ensuring a union is disjoint, we will indifferently either suppose sets are disjoint or rename conflicting object (useful for variables).
 %The disjoint union of two maps \(\varphi: I \to X\) and \(\psi: J \to Y\) with \(I \cap J = \emptyset\) is noted \(\varphi \uplus \psi\) and has the following signature \(I \uplus J \to X \cup Y\).
@@
 \( E=\terms \uplus \actions \uplus \formulas\) .
-\(\terms\) and \(\actions\) are term algebras \TODO{do we explain term algebras}.
+\(\terms\) and \(\actions\) are term algebras.
 The formulas \(\formulas\) contain at least first order formulas and equality\footnote{Equality does not need to be only syntactic.} over \(\terms\) and \(\actions\). 
@@
 
- \(\fvars{e}\) is the set of variables in \(e \in E\) that are not bound by any binder. An expression is closed if \(\fvars{e}=\emptyset\).
+For \(e \in E\),
+ \(\fvars{e}\) is the set of variables in  $e$that are not bound by a binder. An expression is closed if \(\fvars{e}=\emptyset\).
 The set \(\values\) denote values which is a subset of closed terms. \(\rformulas[V]\) is the set of formulas $f$ that only use variables in $V$, i.e. the formulas such that  \(\fvars{f}\subseteq V\).
-
 The substitution in \(e \in E\) of \(x \in \fvars{e}\) by \(t \in \terms\), is denoted \(e\subst{t}{x}\), and its generalisation to the parallel substitution of variables in \(V\) by \(\psi: V \to \terms\) is denoted \(e\psubst{\psi}\).
@@
 \begin{definition}[Open transition, Open automaton (OA)]
-An \emph{open automaton} is a tuple \(\OAg\) with \(S\) the set of states, \(s_0 \in S\) the initial state, \(V\) the finite set of variable names, \(\sigma_0: V' \to \values\) the initial valuation of variables where \(V' \subseteq V\), \(J\) the set of hole names and \(T\) the set of open transitions.
+An \emph{open automaton} is a tuple \(\OAg\) with \(S\) a set of states, \(s_0 \in S\) the initial state, \(V\) the finite set of variable names, \(\sigma_0: V \to \values\) the initial valuation of variables, \(J\) the set of hole names and \(T\) the set of open transitions.
 
@@
 \end{figure}
+\begin{comment}
 \subsection{Reachability : check if useful?}
@@
 We call \emph{non-blocking composition} a composition that can be safely be used to compose open automata that are involved in a deadlock reducing relation.
+
+\end{comment}
 

### 2022-07-01 2021-Refinement/paper/refinementarticle.tex
improvements in sec 3

@@
 %\TODO{useful or not?}
-\begin{definition}[Guard, Out-transition, Transition variables]
+\begin{definition}[Out-transition, Transition variables]
 Let \(V\) be the variable names of the considered automaton, \(T\) its transitions and \(r\) one of its states.
 \(\fOT[T]{r} \in T\) are called the out-transitions of the state \(r\).
-\(\fIT[T]{r} \in T\) are called the in-transitions of the state \(r\).
+%\(\fIT[T]{r} \in T\) are called the in-transitions of the state \(r\).
 When the transition set is clear from the context, it will be omitted.
 The local variables of a transition \(\fvars{t}\) are all variables appearing in transition \(t\) except the global variables of the automaton.
-\begin{align*}
-	\fOT[T]{r} & = \mset{\OTg \in T}{s = r} &
-	\fIT[T]{r} & = \mset{\OTg \in T}{s' = r} \\
-\end{align*}
-\vspace{-1cm}
+%\begin{align*}
+% %&
+%%	\fIT[T]{r} & = \mset{\OTg \in T}{s' = r} \\
+%\end{align*}
+%\vspace{-1cm}
 \begin{mathpar}
-	\fguard{\OTg} \!=\! g \qquad
+%	\fguard{\OTg} \!=\! g \qquad
+	\fOT[T]{r}  = \mset{\OTg \in T}{s = r}
+
 	\fvars{\OTg} \!=\! \mpar{\fvars{\alpha}  \cup \bigcup_{j \in J'} \!\fvars{\beta_j} } \setminus V
@@
 
-The following terminology will be used to reason on open automata
-\begin{definition}[Configuration, instantiated transition]
 A pair consisting of a state and a valuation is called a \emph{configuration}.
-An \emph{instantiated transition} of an automaton \(\OAg\) is a transition  \(t\psi\) where $t\in T$ and $\psi$ is a  well-formed substitution with $\dom(\psi)=vars(t)$. %\setminus V$.
-\end{definition}
+%
+%The following terminology will be used to reason on open automata
+%\begin{definition}[Configuration, instantiated transition]
+%An \emph{instantiated transition} of an automaton \(\OAg\) is a transition  \(t\psi\) where $t\in T$ and $\psi$ is a  well-formed substitution with $\dom(\psi)=vars(t)$. %\setminus V$.
+%\end{definition}
 
@@
 
-Open automata are partially specified automata, that partiality comes mostly from the holes.
-A hole is an interface in which we can plug an open automaton.
+OA are partially specified automata, that partiality comes  from the holes.
+A hole is a port in which we can plug an OA.
 The plugging operation is called composition.
-The composition of open automata was already implicitly defined by the means of composition on pNets in previous work \cite{henrio:01299562} but never completely formalised on open automata.
-The definition of composition below is a direct translation of what happens with pNets composition without the need of introducing pNets.
+The composition of OA was already implicitly defined by the means of composition on pNets in previous work \cite{henrio:01299562} but never  formalised on OA.
+The definition of composition below is a direct translation of what happens with pNets composition without  introducing pNets.
 
@@
 \paragraph{Relations between open automata}
-A relation (bisimulation, refinement, etc.) between open automata requires to compare their states.
-To do so we will suppose that the variables of the two OAs are disjoint (a renaming of variables may have to be applied before comparing OA states).
+A relation (bisimulation, refinement, etc.) between OA requires to compare their states.
+To do so we will suppose that the variables of the two OA are disjoint (a renaming of variables may have to be applied before comparing OA states).
 \begin{definition}[Relation on OA states] Suppose $V_1$ and $V_2$ are disjoint.
@@
 
-\TODO{I do not think we reason on configurations for the moment, if we want to, we should introduce this:}
-Two configurations \(\mpar{s_1, \sigma_1} \in S_1 \times\mpar{V_1 \to \values}, \mpar{s_2, \sigma_2} \in S_2 \times \mpar{V_2 \to \values}\) are related iff \(\sigma_1 \uplus \sigma_2 \vdash R\mpar{s_1, s_2}\).
+%\TODO{I do not think we reason on configurations for the moment, if we want to, we should introduce this:}
+%Two configurations \(\mpar{s_1, \sigma_1} \in S_1 \times\mpar{V_1 \to \values}, \mpar{s_2, \sigma_2} \in S_2 \times \mpar{V_2 \to \values}\) are related iff \(\sigma_1 \uplus \sigma_2 \vdash R\mpar{s_1, s_2}\).
 
@@
 
-Note in this definition, instead of matching an instantiated transition of the first automata to another instantiated transition of the second, it matches an open transition $t_1$ to a family of covering open transitions $t_{2x}^{x\in X}$.
+Note in this definition, instead of matching an instantiated transition (with all variables assigned) of the first automata to another instantiated transition of the second, it matches an open transition $t_1$ to a family of covering open transitions $t_{2x}^{x\in X}$.
 %Note also the second part of the conjunction of condition (2) expresses the deadlock reduction between automata (as introduced in Definition \ref{def:dpwd}).
@@
 
-This concludes for the second case.
+This concludes for the second case and the proof of the theorem.
 
@@
 \end{enumerate}
+\end{document}
+
 \section{Proof of Congruence (Theorem~\ref{thm:Congruence})}

### 2022-07-01 2021-Refinement/paper/refinementarticle.tex
transitivity 3eme item

--- 2022-06-30 2021-Refinement/paper/refinementarticle.tex
@@
 verifying the correctness of programs. By establishing that the
-behaviours of a modified program simulate those of to the source one, simulaiton and bisimulation relations  formalise the desired  relation between a specification and an implementation, 
+behaviours of a modified program simulate those of to the source one,  and bisimulation relations  formalise the desired  relation between a specification and an implementation, 
  two equivalent implementations, or a program and its optimised implementation.
@@
 Automata are convenient for specifying and verifying systems, but most automata definitions allow only the specifications of finite closed systems.
-Indeed those systems are the ones we can veify efficiently, but programming often consist in writing open systems that should be interfaced with others, and with potentially unbound behaviours (at least statically).We investigate in our works the possibility to define open symbolic systems, verify some of their properties, and use them to compose in a structured way more complex systems.
+Indeed those systems are the ones we can verify efficiently, but programming often consist in writing open systems that should be interfaced with others, and with potentially unbound behaviours (at least statically).We investigate in our works the possibility to define open symbolic systems, verify some of their properties, and use them to compose in a structured way more complex systems.
 
@@
 Refinement entails that one system can be considered as a more precise version of the specification, featuring all the specified behaviours with more concrete details.
-In this article we mostly rely on a simulation point of view, where all the specified behaviour must be followed by the refined system but additionla behaviours may exist.
+In this article we mostly rely on a simulation point of view, where all the specified behaviour must be followed by the refined system but additional behaviours may exist.
 However we also ensure that a while scenario, made of several steps, of the specification can also be simulated by the refined system, which is a bit richer than the traditional simulation relation.
@@
 An open automaton \cite{henrio:01299562} is a classical automaton with variables and holes.
-Variables makes autoomata symbolic and allow them to encode infinite state systems.
+Variables makes automata symbolic and allow them to encode infinite state systems.
 Holes enables the composition of automata: an automaton with a hole is an operator that takes another automaton as parameter and reacts to the actions it emits; the composed automaton is a more precise automaton where the behaviour of one ``parameter'' of the main automaton has been provided.
@@
 
-Families of values, or equivalently maps will be noted \(\mset{i \mapsto x_i}{i \in I}\), \(\mset{i \gets x_i}{i \in I}\) or \(x_i^{i \in I}\).
+Families of values, or equivalently maps will be noted \(x_i^{i \in I}\), \(\mset{i \mapsto x_i}{i \in I}\) or \(\mset{i \gets x_i}{i \in I}\).
 % TODO: introduire le fait que \exists c_j^{j \in J} défini J et {j \mapsto c_j}
@@
 \end{multline*}
+
+ Consider $\mpar{s_{1}, s_{3}} \in R_{13}$ then there is a set of states $(s_{2p})^{p\in P}$ of $A_2$ relating  $s_{1}$ and $s_{3}$:
+\[R_{13}(s_1,s_3)=\bigvee_{{p\in P}
+}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}} \]
+
+Let's consider any $s_{2p} \in (s_{2p})^{p\in P}$. According to the refinement relation between  $A_1$ and $A_2$ and Definition \ref{def:preservation} we have:
+
+\begin{multline*}
+\bigforall \mpar{s_1, s_{2p}} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_{2p}} = \mpar{\OTx{1}{}{1}{1}, \OTx{2p}{}{2p}{2p}} \in \fOT{s_1} \times \fOT{s_{2p}} \\ 
+\bigsymb{\bigexists} 
+\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},
+ V_1 \uplus V_2 \uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_{2p}} \vdash \hspace{6cm}\\  R_{12}\mpar{s_1, s_{2p}} \wedge 	g_1 \wedge g_{2p} \wedge \alpha_1 = \alpha_{2p}
+%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2p}} \beta_{1j} = \beta_{2pj} 
+\implies \hspace{6cm}\\
+%\exists
+%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
+\bigsymb{\bigwedge_{x\in X}}
+\mpar{
+\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_{2p} \land \bigwedge_\subbox{j \in J'_{2p} } \beta_{2pj} = \beta_{1xj}\land g_{1 x}\land
+ R_{12}\mpar{s'_{1 x}, s'_{2p}}\psubst{\psi_{1 x} \uplus \psi_{2p}}}
+\end{multline*}
+
+Furthermore, according to the refinement relation between  $A_2$ and $A_3$ and Definition \ref{Def:OA-Refinement} we have  for any open transition $t_{2px}$ in $T_2$ originating from $s_{2p}$ the following:
+\begin{align*}
+\OTx{2p}{x}{2px}{2px} \in \fOT{s_{2p}}
+\end{align*}
+there exists an indexed family of OTs originating from $s_3$: 
+\begin{align*}
+\mpar{\OTx{3}{py}{3py}{3py} \in \fOT{s_3}}^{y \in Y} 
+\end{align*}
+such that $\forall y \in Y, J'_{2p} \cap H = J'_{3py} \cap H$ and
+\begin{multline*}
+%\everymath{\displaystyle}
+V_2 \uplus V_3 \uplus \fvars{t_{2p}} \vdash\\
+R_{23}\mpar{s_{2p}, s_{3}} \wedge g_{2p} \implies  \operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			 \alpha_{2p}=\alpha_{3py} \wedge \bigwedge_\subbox{j \in J'_{3py} \cap H} \beta_{2pj}=\beta_{3pyj} \nwedge \\
+			g_{3py} \wedge R_{23}\mpar{s'_{2p}, s'_{3y}}\psubst{\psi_{2p} \uplus \psi_{3py}}
+		\end{array}}  
+\end{multline*}
+
+Based on             the above two properties, we get:
+\begin{multline*}
+R_{12}\mpar{s_1, s_{2p}} \wedge  R_{23}\mpar{s_{2p}, s_{3}} \wedge	g_1 \wedge g_{2p} \wedge \alpha_1 = \alpha_{2p} 
+%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2p}} \beta_{1j} = \beta_{2pj} 
+\implies \hspace{6cm}\\
+%\exists
+%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
+\bigsymb{\bigwedge_{x\in X}}
+\operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			 \alpha_{2p}=\alpha_{3py} \wedge \bigwedge_\subbox{j \in J'_{3py} \cap H} \beta_{2pj}=\beta_{3pyj} \nwedge \\
+			g_{3py} \wedge R_{23}\mpar{s'_{2p}, s'_{3y}}\psubst{\psi_{2p} \uplus \psi_{3py}}
+		\end{array}}\bigwedge
+\mpar{\everymath{\displaystyle}\begin{array}{l}		
+\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_{2p} \land \bigwedge_\subbox{j \in J'_{2p}} \beta_{2pj} = \beta_{1xj} \land\\ g_{1 x} \land
+ R_{12}\mpar{s'_{1 x}, s'_{2p}}\psubst{\psi_{1 x} \uplus \psi_{2p}}
+ \end{array}}
+ }
+\end{multline*}
+By  rearranging the terms in the formula we get:
+\begin{multline*}
+R_{12}\mpar{s_1, s_{2p}} \wedge  R_{23}\mpar{s_{2p}, s_{3}} \wedge	g_1 \wedge g_{2p} \wedge \operatorname*{\bigsymb{\bigvee}}_{y \in Y}\mpar{ \alpha_1 = \alpha_{2p} \wedge \alpha_{2p}=\alpha_{3py} \wedge g_{3py} }
+%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2p}} \beta_{1j} = \beta_{2pj} 
+\implies \hspace{6cm}\\
+%\exists
+%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
+\bigsymb{\bigwedge_{x\in X}}
+\operatorname*{\bigsymb{\bigvee}}_{y \in Y} 
+\mpar{\everymath{\displaystyle}\begin{array}{l}		
+\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_{2p} \land \bigwedge_\subbox{j \in J'_{2p}} \beta_{2pj} = \beta_{1xj} \land  \bigwedge_\subbox{j \in J'_{3py} \cap H} \beta_{2pj}=\beta_{3pyj} \\ g_{1 x}  \land
+ R_{12}\mpar{s'_{1 x}, s'_{2p}} \wedge R_{23}\mpar{s'_{2p}, s'_{3y}} \psubst{\psi_{1 x} \uplus \psi_{2p}\uplus \psi_{3py}}
+ \end{array}}
+\end{multline*}
+
+The formula is valid for all  $s_{2p} \in (s_{2p})^{p\in P}$. To build $R_{13}$ we need to rely on the disjunction of all possible path to relate $s_1$ and $s_3$:
+\begin{multline*}
+\operatorname*{\bigsymb{\bigvee}}_{p \in P} \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge  R_{23}\mpar{s_{2p}, s_{3}} \wedge	g_1 \wedge g_{2p} \wedge \operatorname*{\bigsymb{\bigvee}}_{y \in Y}\mpar{ \alpha_1 = \alpha_{3py} \wedge g_{3py}}}
+%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2p}} \beta_{1j} = \beta_{2pj} 
+\implies \hspace{6cm}\\
+%\exists
+%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
+\bigsymb{\bigwedge_{x\in X}}
+\operatorname*{\bigsymb{\bigvee}}_{p \in P}\operatorname*{\bigsymb{\bigvee}}_{y \in Y} 
+\mpar{\everymath{\displaystyle}\begin{array}{l}		
+\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_{2p} \land \bigwedge_\subbox{j \in J'_{2p}} \beta_{2pj} = \beta_{1xj} \land  \bigwedge_\subbox{j \in J'_{3py} \cap H} \beta_{2pj}=\beta_{3pyj} \\ g_{1 x}  \land
+ R_{12}\mpar{s'_{1 x}, s'_{2p}} \wedge R_{23}\mpar{s'_{2p}, s'_{3y}} \psubst{\psi_{1 x} \uplus \psi_{2p}\uplus \psi_{3py}}
+ \end{array}}
+\end{multline*}
+
+--------------------------------------
+
 Firstly, according to the refinement relation between  $A_1$ and $A_2$ we have:
@@
 \end{multline*}
-Yet according to the relation between   $A_2$ and $A_3$ we have:
+Yet according to the refinement  relation between   $A_2$ and $A_3$ and Definition \ref{Def:OA-Refinement} we have:
 

### 2022-07-01 2021-Refinement/paper/refinementarticle.tex

--- 2022-07-01 2021-Refinement/paper/refinementarticle.tex
@@
 Automata are convenient for specifying and verifying systems, but most automata definitions allow only the specifications of finite closed systems.
-Indeed those systems are the ones we can veify efficiently, but programming often consist in writing open systems that should be interfaced with others, and with potentially unbound behaviours (at least statically).We investigate in our works the possibility to define open symbolic systems, verify some of their properties, and use them to compose in a structured way more complex systems.
+Indeed those systems are the ones we can verify efficiently, but programming often consist in writing open systems that should be interfaced with others, and with potentially unbound behaviours (at least statically).
+We investigate in our works the possibility to define open symbolic systems, verify some of their properties, and use them to compose in a structured way more complex systems.
+
+Refinement relations verify that and implementation satisfies some properties with respect to a specification.
+Refinement entails that one system can be considered as a more precise version of the specification, featuring all the specified behaviours with more concrete details.
+In this article we mostly rely on a simulation point of view, where all the specified behaviour must be followed by the refined system but additional behaviours may exist.
+However we also ensure that a while scenario, made of several steps, of the specification can also be simulated by the refined system, which is a bit richer than the traditional simulation relation.
 
@@
  This definition, which is based on systems whose behaviour is fully defined, is not well-suited for open systems,  as it requires to reason also about unspecified behaviours.
-In this article we mostly rely on a simulation point of view, where all the specified behaviour must be followed by the refined system but additionla behaviours may exist.
+In this article we mostly rely on a simulation point of view, where all the specified behaviour must be followed by the refined system but additional behaviours may exist.
 However we also ensure that a while scenario, made of several steps, of the specification can also be simulated by the refined system, which is a bit richer than the traditional simulation relation.
@@
 % TODO: introduire le fait que \exists c_j^{j \in J} défini J et {j \mapsto c_j}
+
 %For instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\).

### 2022-07-02 2021-Refinement/paper/refinementarticle.tex
Explanation refinement and preservation prop

@@
 
-Similarly to FH-bisimulation~\cite{fhbisim} we are interested  in finding relations between states of to open automata that contain variables and holes.
-However here we want to build a refinement relation that  also guarantees that no deadlock is introduced when refining the automaton.
+Similarly to FH-bisimulation~\cite{fhbisim} we are interested  in finding relations between states of two open automata that contain variables and holes.
+However here we want to build a refinement relation that  also guarantees that no deadlock is introduced when refining the automaton (at least not among the scenarios originally planned in trhe specification).
 The refinement relation should be conditioned by the internal states of the automata.
@@
 The same problem may arise when two related automata are composed in the same hole of a third one.
+\begin{comment}
 
@@
 }
+USEFUL for context only
 
@@
 An composable automaton cannot transform external non-determinism of the sub-automaton into internal non-determinism.
+
+\end{comment}
 
@@
 
-We first define when a relation is preserved along identical transition deadlock reducing, before characterising a first simple refinement relation  to compare automata with identical holes.
+The idea is that we rely on a classical notion of simulation inspired from~\cite{fh-bisim}.
+The idea is that two states related by a given relation and states that if one state can do a transition, then the other can do a transition too.
+But to limit the creation of deadlock when simulating an automaton, we first define when a relation is preserved along identical transition  before characterising a first simple refinement relation  to compare automata with identical holes.
 
 %\subsection{Deadlock Reduction, Reachability, and Composition}
-\TODO{rewrite}
-A notion that is often used in the context of refinement is the notion of deadlock reduction.
-The objective i that two states related by a given relation and states that if one state can do a transition, then the other can do a transition too.
-What raises this difficulty is the fact that the automaton that simulates a specification features any behaviour that contains the behaviour of the specification but this is only verified at each state of the automaton.
-In this definition, nothing prevents the implementation from adding non-determinism and non-deterministically reaching a deadlock that does not exist in the specification.
-The idea is that simulation states that there is a relation between states such that, for related states, the behaviour of the implementation must follow the behaviour of the specification ...
-but also when both the implementation and the specification do the same transition, they stay related.
+
+Let us first explain the reasons why simulation can introduce deadlocks and how we want too limit them. 
+The automaton that simulates a specification features any behaviour that contains the behaviour of the specification, or more precisely, for each state that simulates a state of the specification, the simulating automaton must at least feature the behaviour of the specification.
+ In this definition, nothing prevents the implementation from adding non-determinism and non-deterministically reaching a state that is unrelated to the specification, this state could be a deadlock even though we only followed transitions that exist in the specification.
+To avoid the appearance of such deadlocks, we will state that, when both the implementation and the specification do the same transition, they stay related.
 This ensures a form of continuity in the comparison in the sense that the refined system is constrained to follow the behaviour of the simulated system along a given scenario. 
 In terms of traces this amounts to some form of deadlock reduction: for each trace followed by the simulated system if the refined system followed the beginning of the trace, it must be able to keep following the trace.
-Except that the notion of trace is insufficient to characterize a scenario of execution in OAs because of the presence of guards, states, and holes.
+Of course, the classical trace view is a simplified view compared to the guards, states and actions from  the holes that exist in OA, but it gives the right intuition.
 
@@
 
+We thus define the following property that can be understood as follows.
+Take a specification automaton and its implementation.
+Consider two related states for the refinement relation.
+Suppose an identical transition exist in both automata (with same guards and same label), then either the reached states $s_1'$ and $s_2'$ are related by refinement, or there exists another transition of the specification that is also identical and leads to a state $s_1''$ that is related to $s_2'$ in the refinement relation.
+Finally, we should take into account that 1) instead of equality, we should check if there is a state such that both transitions are feasible (the conjunction of guards is satisfiable), and that  2)instead of finding another transition of the specification we might find a family of transitions that cover all the cases of the transition of the implementation.
+This leads us to the following definition.
 \begin{definition}[Preservation along identical transitions]\label{def:preservation} \\

### 2022-07-04 2021-Refinement/paper/refinementarticle.tex
Example...

@@
 
-In Fig.
-\ref{Fig:SpecOA} we present a very simple example of an open automaton inspired from \cite{Gorrieri:2001}.
-An automaton that we name \texttt{database} modelling a data base that can be queried and updated.
-The open automaton \texttt{counter}    depicting  the behaviour of the timer is illustrated in Fig.
-\ref{Fig:counter}.
-
+\begin{example} As a running example, we consider a data base example inspired from \cite{Gorrieri:2001}.
+The open automaton \texttt{database}  modelling its behaviour is depicted in Fig.
+\ref{Fig:SpecOA}.
+The \texttt{database} can be queried using an operation \texttt{qry} and updated using an operation \texttt{upd}.
+The associated automaton has a single hole:  a counter ($\texttt{cnt}$)  depicting  the behaviour of the timer.
+When the \texttt{database}  performs a query,  it sets the new time limit of the counter component and the exposed action to the environment is an observable  action \texttt{qry}.
+The \texttt{database} updates and  switches when it agrees with the counter component the time is over, and the exposed action is \texttt{upd}.
+The open automaton \texttt{counter}    depicting  the behaviour of the timer is illustrated in Fig. \ref{Fig:counter}. 
+\end{example}
 \begin{figure}[h]
@@
    \caption{Open Automaton of \texttt{counter} process (left).
-Its role is to get a target, then count ticks until that target is reached, then emit an action with the elapsed time and restart.
+Its role is to get a target, then count ticks until that target is reached, then emits an action with the elapsed time and restart.
 And Open Automation of  the composition \texttt{database}[\texttt{counter}] (right).\label{Fig:counter}}
 \end{figure}
-
 \paragraph{Relations between open automata}

### 2022-07-06 2021-Refinement/paper/refinementarticle.tex
un petit comment Def 7

@@
 \begin{example} As a running example, we consider a data base example inspired from \cite{Gorrieri:2001}.
-The open automaton \texttt{database}  modelling its behaviour is depicted in Fig.
+The open automaton \texttt{database}  modelling the behaviour of data base is depicted in Fig.
 \ref{Fig:SpecOA}.
@@
 
-\subsection{Example}
-
-As an example, the traffic light system  that controls  
- traffic at an intersection. The open automaton  
-modeling this system  is illustrated in  Figure \ref{fig:tls}. This automaton has three states  remembering which coloured light
-is on (Red, Yellow or Green).
-It includes two holes: a controller ($\symb{ctl}$) and a counter ($\symb{cnt}$)  depicting together the behaviour of the timer.
-The color switches when the counter and the controller component agree that the time is over.
-The new time limit can be set by the counter component and the exposed action to the environment is an unobservable  action $\tau$.
-
-The open automata shown in Figure  \ref{fig:ctlandcnt} models  the timer.
-On the left, the controller component designed to be connected in the hole $\symb{ctl}$.
-Its role is to decide the duration before switching the lights.
-We control the time interval for each light by setting them by prior knowledge:  17s for the first duration, 3s for the second, and 20s for the third.
-On the right, the tick counter component designed to be connected in the hole $\symb{cnt}$.
-
-In Figure \ref{fig:tlf} we present the composition of the three automata.
-Each state of the result of the composition consists  of  a state of traffic light system together with a state of controller component and one of counter component.
-The composed automaton  takes over  the same steps as the traffic light automaton but it also includes new steps,  indicting the change of states for the setting of timer.
-Its $\tau$ transitions involve both the traffic light automaton and the hole  automata, they correspond to  a joint step of  sending time thresholds of the controller, the time setting of the counter.
-For instance, the  $\tau$  transition starting from \(R1S\), it is obtained by composition of both
-\nmm{\OT{R}{R}{\tau}{\mbrc{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}, \nmm{\OT{1}{2}{\theta\mpar{17}}{\mbrc{}}{\top}{\mbrc{}}} and   \nmm{\OT{S}{C}{\act{set}\mpar{x}}{\mbrc{}}{\top}{\mbrc{t \gets x, c \gets 0}}}.
-\\
-However, the joint composition of transitions  \nmm{\OT{R}{R}{\tau}{\mbrc{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}, \nmm{\OT{2}{3}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} and
-\nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} is not agreed because it would produce a transition whose guard is not satisfiable.
-It will produce the following transition: \nmm{\OT{R2C}{R3C}{\tau}{\mbrc{}}{\top \wedge \top \wedge c < t \wedge \act{set}\mpar{x} = \act{tick} \wedge \theta\mpar{x} = \delta\mpar{x}}{\mbrc{c \gets c + 1}}} which requires to be triggered  the equality of completely different actions.
-
-\begin{figure}[!tb]
-\centering
-\scalebox{.75}{\input{Traffic_Lights_Spec.tex}}
-\caption{The specification of a Traffic Light system}
-\label{fig:tls}
-\end{figure}
-
-\begin{figure}[!tb]
-%\centering
-\scalebox{.75}{\input{Traffic_Lights_Controller.tex}}
-\scalebox{.75}{\input{Traffic_Lights_Register.tex}}
-\caption{(a) An example of controller component ~~  (b) An example of counter component}
-\label{fig:ctlandcnt}
-\end{figure}
-
-\begin{figure}[!tb]
-\centering
-\scalebox{.75}{\input{Traffic_Lights_Interm.tex}}
-\caption{The incomplete Specification Traffic Lights system}
-\label{fig:tlf}
-\end{figure}
-
-\begin{figure}[!tb]
-\centering
-\scalebox{.75}{\input{Traffic_Lights_Full.tex}}
-\caption{The full Traffic Lights system}
-\label{fig:tlf}
-\end{figure}
 \begin{comment}
@@
 \end{definition}
+
 Reachability takes into account all paths, and can over-approximate the reachable configurations. 
@@
 
+This definition leads to a notion of simulation as refinement the same as the one used in LOTOS??? and presented under the name extension refinement.
+The extension consists in adding new functionalities by preserving existing ones.
+Indeed, in case there is no hole and no guard, i.e., in case the definitions of open automata coincide with those of automata, the relation allows new behaviour to be added in terms of new traces, but doesn't allow new deadlocks to
+be added, i.e., for traces of the specification (abstract automaton) the implementation (refined automaton) must not add
+deadlocks.
+
 \TODO{
@@
 \appendix
+
+\subsection{Example}
+
+As an example, the traffic light system  that controls  
+ traffic at an intersection. The open automaton  
+modeling this system  is illustrated in  Figure \ref{fig:tls}. This automaton has three states  remembering which coloured light
+is on (Red, Yellow or Green).
+It includes two holes: a controller ($\symb{ctl}$) and a counter ($\symb{cnt}$)  depicting together the behaviour of the timer.
+The color switches when the counter and the controller component agree that the time is over.
+The new time limit can be set by the counter component and the exposed action to the environment is an unobservable  action $\tau$.
+
+The open automata shown in Figure  \ref{fig:ctlandcnt} models  the timer.
+On the left, the controller component designed to be connected in the hole $\symb{ctl}$.
+Its role is to decide the duration before switching the lights.
+We control the time interval for each light by setting them by prior knowledge:  17s for the first duration, 3s for the second, and 20s for the third.
+On the right, the tick counter component designed to be connected in the hole $\symb{cnt}$.
+
+In Figure \ref{fig:tlf} we present the composition of the three automata.
+Each state of the result of the composition consists  of  a state of traffic light system together with a state of controller component and one of counter component.
+The composed automaton  takes over  the same steps as the traffic light automaton but it also includes new steps,  indicting the change of states for the setting of timer.
+Its $\tau$ transitions involve both the traffic light automaton and the hole  automata, they correspond to  a joint step of  sending time thresholds of the controller, the time setting of the counter.
+For instance, the  $\tau$  transition starting from \(R1S\), it is obtained by composition of both
+\nmm{\OT{R}{R}{\tau}{\mbrc{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}, \nmm{\OT{1}{2}{\theta\mpar{17}}{\mbrc{}}{\top}{\mbrc{}}} and   \nmm{\OT{S}{C}{\act{set}\mpar{x}}{\mbrc{}}{\top}{\mbrc{t \gets x, c \gets 0}}}.
+\\
+However, the joint composition of transitions  \nmm{\OT{R}{R}{\tau}{\mbrc{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}, \nmm{\OT{2}{3}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} and
+\nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} is not agreed because it would produce a transition whose guard is not satisfiable.
+It will produce the following transition: \nmm{\OT{R2C}{R3C}{\tau}{\mbrc{}}{\top \wedge \top \wedge c < t \wedge \act{set}\mpar{x} = \act{tick} \wedge \theta\mpar{x} = \delta\mpar{x}}{\mbrc{c \gets c + 1}}} which requires to be triggered  the equality of completely different actions.
+
+\begin{figure}[!tb]
+\centering
+\scalebox{.75}{\input{Traffic_Lights_Spec.tex}}
+\caption{The specification of a Traffic Light system}
+\label{fig:tls}
+\end{figure}
+
+\begin{figure}[!tb]
+%\centering
+\scalebox{.75}{\input{Traffic_Lights_Controller.tex}}
+\scalebox{.75}{\input{Traffic_Lights_Register.tex}}
+\caption{(a) An example of controller component ~~  (b) An example of counter component}
+\label{fig:ctlandcnt}
+\end{figure}
+
+\begin{figure}[!tb]
+\centering
+\scalebox{.75}{\input{Traffic_Lights_Interm.tex}}
+\caption{The incomplete Specification Traffic Lights system}
+\label{fig:tlf}
+\end{figure}
+
+\begin{figure}[!tb]
+\centering
+\scalebox{.75}{\input{Traffic_Lights_Full.tex}}
+\caption{The full Traffic Lights system}
+\label{fig:tlf}
+\end{figure}
 

### 2022-07-07 2021-Refinement/paper/refinementarticle.tex
meeting notes

@@
 
-\section{Related Work}
-\label{sec:sota}
-
-\TODO{1 page}
-\TODO{move to the end?}
-
-There are some works that have focused on  the refinement of open systems. Defining refinement of open systems as trace inclusion  is  addressed  as a notion of subtyping in type theory 
-\cite{GayH:2005,BravettiZ:2021}.
-Such refinement is  instead based  on interface-oriented approach, it allows the expression more internal choices and less external choices.
-The refinement of open systems is also defined in terms of  alternating simulation \cite{Alur:1998,deAlfaro:2021}, which deals with game-based models.
-Alternating simulation that is originating from the game theory \cite{deAlfaro:2003} allows  the study of relation between individual components by viewing them as alternating transition systems.
-In particular,  a refinement of game-based automata expresses that the refined component can offer more services (input actions) and fewer service demands (output actions).
-However, the composition of such automata may
-lead to illegal states, where one automaton issues an output that is not acceptable as input in the other one.
-The theory of alternating simulation provides an optimistic approach to compute compatibility between automata based on the fact that each automaton expects the other to provide  legal inputs, i.e, two components can be composed if there is an environment where they can work together.
-As we shall see in this paper,
-our approach to design refinement  has some commonalities with that of the above mentioned \cite{deAlfaro:2021}: both are process-oriented approach even if they are not based on the same notion of simulation and they are based on optimistic approach to composition.
-For the composability, we shall see that we use the notion of comparability of holes (similar to the notion of compatibility), which is explicitly encompassed in the definition of composition.
-
-Previous work on open automata focused on equivalence relations compatible with composition.
-In an article by Hou, Zechen and Madelaine \cite{10.1145/3372884.3373161}, a computable bisimulation is introduced and proved equivalent to the previous bisimulation already introduced.
-In a more recent work by Ameur-Boulifa, Henrio and Madelaine \cite{fhbisim}, a weak version of the bisimulation on open automata is introduced.
-These works differ from ours because the relation introduced in this report is a refinement relation in the form of a simulation and not a bisimulation.
-Also we do not have results as strong as computability neither a weak version able to tackle silent actions.
-
-\TODO{Some related work on other models than open automata introduce refinement relations.
-In a chapter by Bellegarde, Julliand and Kouchnarenko \cite{10.1007/3-540-46428-X_19}, a simulation relation on transition systems is introduced.
-This simulation encompass action refinement, is able to deal with silent actions and is compatible with parallel composition.
-Here the refinement relation does not consider action refinement as valid but it should be done in future work.
-Also they check how LTL properties are preserved or combined using their refinement which we do not do.
-However their model is less expressive: the transition system model is less expressive than open automata and the parallel composition is less expressive than composition on open automata.
-In a later report by Kouchnarenko and Lanoix \cite{10.1007/978-3-540-70881-0_26}, the refinement relation they introduce is on LTS (labelled transition systems).
-Their relation additionally prevents deadlock and livelocks.
-The composition is also extended to synchronised composition which is more expressive.
-In our work we also deal with deadlocks but not with livelocks since the latter arise only with silent actions.
-This work is closer than the previous one to what we do here, still open automata are more expressive than LTS and composition is more general than synchronised composition.}
-
-A refinement relation on models nearer to open automata is introduced in an article by Zhang, Meng and Lo \cite{Zhang2014}.
-In their article they work with transition systems with variable which makes the state space potentially infinite.
-This aspect is also present in open automata.
-They show how invariants are composed.
-By relation on these invariants they introduce several refinement relations.
-We could have done something similar for non-blocking composition reachability predicates which are introduced in Section \ref{sec:proofelts}.
-
-On the deadlock prevention aspect, an article by Dihego, Sampaio and Oliveira \cite{DIHEGO2020110598} present a refinement relation on process algebra (translated to LTS).
-This refinement relation is a special case of inheritance and prevents the introduction of deadlocks.
-Their refinement and inheritance are quite the opposite of our refinement in terms of new behaviours.
-They have channels, interfaces, inputs and outputs, which in the open automata model can be compared to action labels, holes and action data for both inputs and outputs.
-They have a rich composition as open automata but the introduction of deadlock is already prevented by a well chosen set of composing operations.
-Also their composition is slightly different than the one on open automata because they can cause loops by linking two channels of the same process, where in open automata the composition makes an oriented tree.
-In their model there is an explicit deadlock and a successful termination where in open automata there are no explicit termination.
-We define a deadlock as a configuration without possible transition and assume what is a deadlock when comparing the open automata.
-To define their refinement and inheritance relation they use trace and failure semantics, which are weaker than (bi)simulations \cite{10.5555/640428.640430} and could break with open automata composition.
-
 \section{Open Automata and their Composition}\label{sec:background}
@@
 \subsection{Preliminaries and notations}
-Families of values, or equivalently maps will be noted \(\mset{i \mapsto x_i}{i \in I}\), or \(\mset{i \gets x_i}{i \in I}\), or \(x_i^{i \in I}\) depending on what is more convenient.
+Families of values, or equivalently maps will be noted \(x_i^{i \in I}\), \(\mset{i \mapsto x_i}{i \in I}\), or \(\mset{i \gets x_i}{i \in I}\), depending on what is more convenient.
 % TODO: introduire le fait que \exists c_j^{j \in J} défini J et {j \mapsto c_j}
-
 %For instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\).
@@
 Its role is to get a target, then count ticks until that target is reached, then emits an action with the elapsed time and restart.
-And Open Automation of  the composition \texttt{database}[\texttt{counter}] (right).\label{Fig:counter}}
+And Open Automation of  the composition \texttt{database}[\texttt{counter/cnt}] (right).\label{Fig:counter}}
 \end{figure}
@@
 
-TODO OR NOT?
+Bisimulation between OA was defined in~\cite{fh-bisim}. Instead of recalling its definition we show below the principles of this bisimulation.
+
+\begin{tikzpicture}
+  \node[state,inner sep=5pt,minimum size=10pt] (1) {$s$};
+  \node[state,inner sep=5pt,minimum size=10pt, below right of=1,right=80pt] (2) {$t$};
+  \node[state,inner sep=5pt,minimum size=10pt, above right of=1,right=80pt] (3) {$t'$};
+
+  \draw (1) edge[align=center] node[below]{\OT{}{}{\alpha(x)}{h\mapsto\beta(x)}{x<0}{y\leftarrow -x}}  (2);
+  \draw (1) edge[align=center] node[above]{\OT{}{}{\alpha(x)}{h\mapsto\beta(x)}{x\geq 0}{y\leftarrow x}} (3);
+\end{tikzpicture}
+\begin{tikzpicture}
+  \node[state,inner sep=5pt,minimum size=10pt] (1) {$s_2$};
+  \node[state,inner sep=5pt,minimum size=10pt,  right of=1,right=90pt] (2) {$t_2$};
+
+  \draw (1) edge[align=center] node[below]{\OT{}{}{\alpha(x)}{h\mapsto\beta(x)}{x<0}{y\leftarrow -x}}  (2);
+  \draw (1) edge[align=center] node[above]{\OT{}{}{\alpha(x)}{h\mapsto\beta(x)}{x\geq 0}{y\leftarrow x}} (3);
+\end{tikzpicture}
 
@@
 - relation with fh bisimulation
+
+\section{Related Work}
+\label{sec:sota}
+
+\TODO{1 page}
+
+There are some works that have focused on  the refinement of open systems. Defining refinement of open systems as trace inclusion  is  addressed  as a notion of subtyping in type theory 
+\cite{GayH:2005,BravettiZ:2021}.
+Such refinement is  instead based  on interface-oriented approach, it allows the expression more internal choices and less external choices.
+The refinement of open systems is also defined in terms of  alternating simulation \cite{Alur:1998,deAlfaro:2021}, which deals with game-based models.
+Alternating simulation that is originating from the game theory \cite{deAlfaro:2003} allows  the study of relation between individual components by viewing them as alternating transition systems.
+In particular,  a refinement of game-based automata expresses that the refined component can offer more services (input actions) and fewer service demands (output actions).
+However, the composition of such automata may
+lead to illegal states, where one automaton issues an output that is not acceptable as input in the other one.
+The theory of alternating simulation provides an optimistic approach to compute compatibility between automata based on the fact that each automaton expects the other to provide  legal inputs, i.e, two components can be composed if there is an environment where they can work together.
+As we shall see in this paper,
+our approach to design refinement  has some commonalities with that of the above mentioned \cite{deAlfaro:2021}: both are process-oriented approach even if they are not based on the same notion of simulation and they are based on optimistic approach to composition.
+For the composability, we shall see that we use the notion of comparability of holes (similar to the notion of compatibility), which is explicitly encompassed in the definition of composition.
+
+Previous work on open automata focused on equivalence relations compatible with composition.
+In an article by Hou, Zechen and Madelaine \cite{10.1145/3372884.3373161}, a computable bisimulation is introduced and proved equivalent to the previous bisimulation already introduced.
+In a more recent work by Ameur-Boulifa, Henrio and Madelaine \cite{fhbisim}, a weak version of the bisimulation on open automata is introduced.
+These works differ from ours because the relation introduced in this report is a refinement relation in the form of a simulation and not a bisimulation.
+Also we do not have results as strong as computability neither a weak version able to tackle silent actions.
+
+\TODO{Some related work on other models than open automata introduce refinement relations.
+In a chapter by Bellegarde, Julliand and Kouchnarenko \cite{10.1007/3-540-46428-X_19}, a simulation relation on transition systems is introduced.
+This simulation encompass action refinement, is able to deal with silent actions and is compatible with parallel composition.
+Here the refinement relation does not consider action refinement as valid but it should be done in future work.
+Also they check how LTL properties are preserved or combined using their refinement which we do not do.
+However their model is less expressive: the transition system model is less expressive than open automata and the parallel composition is less expressive than composition on open automata.
+In a later report by Kouchnarenko and Lanoix \cite{10.1007/978-3-540-70881-0_26}, the refinement relation they introduce is on LTS (labelled transition systems).
+Their relation additionally prevents deadlock and livelocks.
+The composition is also extended to synchronised composition which is more expressive.
+In our work we also deal with deadlocks but not with livelocks since the latter arise only with silent actions.
+This work is closer than the previous one to what we do here, still open automata are more expressive than LTS and composition is more general than synchronised composition.}
+
+A refinement relation on models nearer to open automata is introduced in an article by Zhang, Meng and Lo \cite{Zhang2014}.
+In their article they work with transition systems with variable which makes the state space potentially infinite.
+This aspect is also present in open automata.
+They show how invariants are composed.
+By relation on these invariants they introduce several refinement relations.
+We could have done something similar for non-blocking composition reachability predicates which are introduced in Section \ref{sec:proofelts}.
+
+On the deadlock prevention aspect, an article by Dihego, Sampaio and Oliveira \cite{DIHEGO2020110598} present a refinement relation on process algebra (translated to LTS).
+This refinement relation is a special case of inheritance and prevents the introduction of deadlocks.
+Their refinement and inheritance are quite the opposite of our refinement in terms of new behaviours.
+They have channels, interfaces, inputs and outputs, which in the open automata model can be compared to action labels, holes and action data for both inputs and outputs.
+They have a rich composition as open automata but the introduction of deadlock is already prevented by a well chosen set of composing operations.
+Also their composition is slightly different than the one on open automata because they can cause loops by linking two channels of the same process, where in open automata the composition makes an oriented tree.
+In their model there is an explicit deadlock and a successful termination where in open automata there are no explicit termination.
+We define a deadlock as a configuration without possible transition and assume what is a deadlock when comparing the open automata.
+To define their refinement and inheritance relation they use trace and failure semantics, which are weaker than (bi)simulations \cite{10.5555/640428.640430} and could break with open automata composition.
 

### 2022-07-07 2021-Refinement/paper/refinementarticle.tex
biblio

@@
 
-This definition leads to a notion of simulation as refinement the same as the one used in LOTOS??? and presented under the name extension refinement.
+This definition leads to a notion of simulation as refinement the same as the one used in LOTOS \cite{Brinksma:87} and presented under the name extension refinement.
 The extension consists in adding new functionalities by preserving existing ones.

### 2022-07-08 2021-Refinement/paper/refinementarticle.tex
figures

@@
 Its role is to get a target, then count ticks until that target is reached, then emits an action with the elapsed time and restart.
-And Open Automation of  the composition \texttt{database}[\texttt{counter/cnt}] (right).\label{Fig:counter}}
+And Open Automaton of  the composition \texttt{database}[\texttt{counter/cnt}] (right).\label{Fig:counter}}
 \end{figure}
+In Fig.
+\ref{Fig:counter} (right) we present the composition \texttt{database}[\texttt{counter/cnt}] of the two open automata \texttt{database} and \texttt{counter}.
+Each state of the composite consists of a state of \texttt{database} together with a state of \texttt{counter}.
+The composed automaton  takes over  the same steps as the   \texttt{database} automaton but it also includes new steps,  indicting the change of states for the setting of timer.
+
 \paragraph{Relations between open automata}
@@
 
+\begin{figure}[h]
+ \centering
+   \includegraphics[width=.6\textwidth]{Figures/composeRefined.pdf}
+   \caption{The refined Open Automaton composed with the counter \label{Fig:ComposeRefine}}
+\end{figure}
+
 \section{A Refinement Relation that Takes Holes into Account}\label{sec:holes}
@@
 \begin{center}
-\includegraphics[scale=0.7]{Figures/Theorem2}
+\includegraphics[scale=0.7]{Figures/Theorem2bis}
 \end{center}
@@
 \appendix
-
-\subsection{Example}
-
-As an example, the traffic light system  that controls  
- traffic at an intersection. The open automaton  
-modeling this system  is illustrated in  Figure \ref{fig:tls}. This automaton has three states  remembering which coloured light
-is on (Red, Yellow or Green).
-It includes two holes: a controller ($\symb{ctl}$) and a counter ($\symb{cnt}$)  depicting together the behaviour of the timer.
-The color switches when the counter and the controller component agree that the time is over.
-The new time limit can be set by the counter component and the exposed action to the environment is an unobservable  action $\tau$.
-
-The open automata shown in Figure  \ref{fig:ctlandcnt} models  the timer.
-On the left, the controller component designed to be connected in the hole $\symb{ctl}$.
-Its role is to decide the duration before switching the lights.
-We control the time interval for each light by setting them by prior knowledge:  17s for the first duration, 3s for the second, and 20s for the third.
-On the right, the tick counter component designed to be connected in the hole $\symb{cnt}$.
-
-In Figure \ref{fig:tlf} we present the composition of the three automata.
-Each state of the result of the composition consists  of  a state of traffic light system together with a state of controller component and one of counter component.
-The composed automaton  takes over  the same steps as the traffic light automaton but it also includes new steps,  indicting the change of states for the setting of timer.
-Its $\tau$ transitions involve both the traffic light automaton and the hole  automata, they correspond to  a joint step of  sending time thresholds of the controller, the time setting of the counter.
-For instance, the  $\tau$  transition starting from \(R1S\), it is obtained by composition of both
-\nmm{\OT{R}{R}{\tau}{\mbrc{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}, \nmm{\OT{1}{2}{\theta\mpar{17}}{\mbrc{}}{\top}{\mbrc{}}} and   \nmm{\OT{S}{C}{\act{set}\mpar{x}}{\mbrc{}}{\top}{\mbrc{t \gets x, c \gets 0}}}.
-\\
-However, the joint composition of transitions  \nmm{\OT{R}{R}{\tau}{\mbrc{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}, \nmm{\OT{2}{3}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} and
-\nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} is not agreed because it would produce a transition whose guard is not satisfiable.
-It will produce the following transition: \nmm{\OT{R2C}{R3C}{\tau}{\mbrc{}}{\top \wedge \top \wedge c < t \wedge \act{set}\mpar{x} = \act{tick} \wedge \theta\mpar{x} = \delta\mpar{x}}{\mbrc{c \gets c + 1}}} which requires to be triggered  the equality of completely different actions.
-
-\begin{figure}[!tb]
-\centering
-\scalebox{.75}{\input{Traffic_Lights_Spec.tex}}
-\caption{The specification of a Traffic Light system}
-\label{fig:tls}
-\end{figure}
-
-\begin{figure}[!tb]
-%\centering
-\scalebox{.75}{\input{Traffic_Lights_Controller.tex}}
-\scalebox{.75}{\input{Traffic_Lights_Register.tex}}
-\caption{(a) An example of controller component ~~  (b) An example of counter component}
-\label{fig:ctlandcnt}
-\end{figure}
-
-\begin{figure}[!tb]
-\centering
-\scalebox{.75}{\input{Traffic_Lights_Interm.tex}}
-\caption{The incomplete Specification Traffic Lights system}
-\label{fig:tlf}
-\end{figure}
-
-\begin{figure}[!tb]
-\centering
-\scalebox{.75}{\input{Traffic_Lights_Full.tex}}
-\caption{The full Traffic Lights system}
-\label{fig:tlf}
-\end{figure}
 
@@
 
+\section{Example}
+
+As an example, the traffic light system  that controls  
+ traffic at an intersection. The open automaton  
+modeling this system  is illustrated in  Figure \ref{fig:tls}. This automaton has three states  remembering which coloured light
+is on (Red, Yellow or Green).
+It includes two holes: a controller ($\symb{ctl}$) and a counter ($\symb{cnt}$)  depicting together the behaviour of the timer.
+The color switches when the counter and the controller component agree that the time is over.
+The new time limit can be set by the counter component and the exposed action to the environment is an unobservable  action $\tau$.
+
+The open automata shown in Figure  \ref{fig:ctlandcnt} models  the timer.
+On the left, the controller component designed to be connected in the hole $\symb{ctl}$.
+Its role is to decide the duration before switching the lights.
+We control the time interval for each light by setting them by prior knowledge:  17s for the first duration, 3s for the second, and 20s for the third.
+On the right, the tick counter component designed to be connected in the hole $\symb{cnt}$.
+
+In Figure \ref{fig:tlf} we present the composition of the three automata.
+Each state of the result of the composition consists  of  a state of traffic light system together with a state of controller component and one of counter component.
+The composed automaton  takes over  the same steps as the traffic light automaton but it also includes new steps,  indicting the change of states for the setting of timer.
+Its $\tau$ transitions involve both the traffic light automaton and the hole  automata, they correspond to  a joint step of  sending time thresholds of the controller, the time setting of the counter.
+For instance, the  $\tau$  transition starting from \(R1S\), it is obtained by composition of both
+\nmm{\OT{R}{R}{\tau}{\mbrc{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}, \nmm{\OT{1}{2}{\theta\mpar{17}}{\mbrc{}}{\top}{\mbrc{}}} and   \nmm{\OT{S}{C}{\act{set}\mpar{x}}{\mbrc{}}{\top}{\mbrc{t \gets x, c \gets 0}}}.
+\\
+However, the joint composition of transitions  \nmm{\OT{R}{R}{\tau}{\mbrc{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}, \nmm{\OT{2}{3}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} and
+\nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} is not agreed because it would produce a transition whose guard is not satisfiable.
+It will produce the following transition: \nmm{\OT{R2C}{R3C}{\tau}{\mbrc{}}{\top \wedge \top \wedge c < t \wedge \act{set}\mpar{x} = \act{tick} \wedge \theta\mpar{x} = \delta\mpar{x}}{\mbrc{c \gets c + 1}}} which requires to be triggered  the equality of completely different actions.
+
+\begin{figure}[!tb]
+\centering
+\scalebox{.75}{\input{Traffic_Lights_Spec.tex}}
+\caption{The specification of a Traffic Light system}
+\label{fig:tls}
+\end{figure}
+
+\begin{figure}[!tb]
+%\centering
+\scalebox{.75}{\input{Traffic_Lights_Controller.tex}}
+\scalebox{.75}{\input{Traffic_Lights_Register.tex}}
+\caption{(a) An example of controller component ~~  (b) An example of counter component}
+\label{fig:ctlandcnt}
+\end{figure}
+
+\begin{figure}[!tb]
+\centering
+\scalebox{.75}{\input{Traffic_Lights_Interm.tex}}
+\caption{The incomplete Specification Traffic Lights system}
+\label{fig:tlf}
+\end{figure}
+
+\begin{figure}[!tb]
+\centering
+\scalebox{.75}{\input{Traffic_Lights_Full.tex}}
+\caption{The full Traffic Lights system}
+\label{fig:tlf}
+\end{figure}
+
 \end{document}

### 2022-07-10 2021-Refinement/paper/refinementarticle.tex
Petites corrections grammaticales sur les 2 premieres pages, et quelques questions (codees par \TODO)

@@
 
-Establishing equivalences and refinement relations between programs is an important mean for 
+Establishing equivalence and refinement relations between programs is an important mean for 
 verifying the correctness of programs. By establishing that the
-behaviours of a modified program simulate those of to the source one,  and bisimulation relations  formalise the desired  relation between a specification and an implementation, 
+behaviours of a modified program simulate those of the source one,  and bisimulation relations  formalise the desired  relation between a specification and an implementation, 
  two equivalent implementations, or a program and its optimised implementation.
@@
 
-We define several variants of refinement between systems including either equal or different sets of holes, and 
+We define several variants of refinement relations between systems including either equal or different sets of holes, and 
 show under which conditions these refinements are preserved by composition of open automata.
@@
 Automata are convenient for specifying and verifying systems, but most automata definitions allow only the specifications of finite closed systems.
-Indeed those systems are the ones we can verify efficiently, but programming often consist in writing open systems that should be interfaced with others, and with potentially unbound behaviours (at least statically).
+Indeed those systems are the ones we can verify efficiently, but programming often consists in writing open systems that should be interfaced with others, and with potentially unbound behaviours (at least statically).
 We investigate in our works the possibility to define open symbolic systems, verify some of their properties, and use them to compose in a structured way more complex systems.
 
-Refinement relations verify that and implementation satisfies some properties with respect to a specification.
+Refinement relations verify that an implementation satisfies some properties with respect to a specification.
 Refinement entails that one system can be considered as a more precise version of the specification, featuring all the specified behaviours with more concrete details.
 In this article we mostly rely on a simulation point of view, where all the specified behaviour must be followed by the refined system but additional behaviours may exist.
-However we also ensure that a while scenario, made of several steps, of the specification can also be simulated by the refined system, which is a bit richer than the traditional simulation relation.
+However we also ensure that a whole scenario, made of several steps, of the specification can also be simulated by the refined system, which is slightly richer than the traditional simulation relation.
 
@@
  It is usually defined as trace inclusion or simulation  \cite{Milner:1980,Kouchnarenko:2007}; this ensures that all behaviours of the implementation must be also behaviours of the specification.
+\TODO{heu c'est pas le contraire, l'implem (le "refined"), peut avoir plus de comportements que la spec, non ?}
  This definition, which is based on systems whose behaviour is fully defined, is not well-suited for open systems,  as it requires to reason also about unspecified behaviours.
-In this article we mostly rely on a simulation point of view, where all the specified behaviour must be followed by the refined system but additional behaviours may exist.
-However we also ensure that a while scenario, made of several steps, of the specification can also be simulated by the refined system, which is a bit richer than the traditional simulation relation.
+In this article we mostly rely on a simulation point of view, where all the specified behaviours must be followed by the refined system but additional behaviours may exist.
+\TODO{the following sentence is a copy of the previous paragraph !} However we also ensure that a whole scenario, made of several steps, of the specification can also be simulated by the refined system, which is a bit richer than the traditional simulation relation.
 
@@
 An open automaton \cite{henrio:01299562} is a classical automaton with variables and holes.
-Variables makes automata symbolic and allow them to encode infinite state systems.
-Holes enables the composition of automata: an automaton with a hole is an operator that takes another automaton as parameter and reacts to the actions it emits; the composed automaton is a more precise automaton where the behaviour of one ``parameter'' of the main automaton has been provided.
+Variables make automata symbolic and allow them to encode infinite state systems.
+Holes enable the composition of automata: an automaton with a hole is an operator that takes another automaton as parameter and reacts to the actions it emits; the composed automaton is a more precise automaton where the behaviour of one ``parameter'' \TODO{est-ce qu'on n'ecrirait pas ici "process parameter" pour les distinguer des variables standard ?} of the main automaton has been provided.
 
@@
 
-This article first introduces open automata that were defined in  \cite{henrio:01299562},  but compared to previous works, we additionally define the composition of open automata.
+This article first introduces open automata that were defined in  \cite{henrio:01299562}. %,  but compared to previous works, we 
+and additionaly defines the composition of open automata.
 Then we define  a refinement relation for open automata that has the following characteristics:
@@
 \item Good properties relatively to composition: we prove here that filling the same hole  with the same automaton preserves the refinement relation.
-\item Ability to take into account both composition and transitivity: this is a challenge because composition changes the set of holes of the open automaton and refinement takes into account actions of the holes.
+\item Ability to take into account both composition and transitivity: this is a challenge because composition changes the set of holes of the open automaton and refinement takes into account the actions of the holes.
 \end{itemize}
@@
 The following of this article is organised as follows. 
-We first review related works in Section~\ref{sec:sota}; then Section~\ref{sec:background} recalls the definition of open automata and defines their composition. 
-We  then  define a refinement relation for open automata, first only considering two automata with the same set of holes in Section~\ref{sec:refinement} and generalize it to automataa with a different set of holes in Section~\ref{sec:holes} before proving basic properties of refinement in Section~\ref{sec:prop}; here we prove that refinement is a preorder and we focus on one composition property.
-Section~\ref{sec:ccl} concludes the paper.
+Section~\ref{sec:background} recalls the definition of open automata and defines their composition. 
+We  then  define a refinement relation for open automata, first only considering two automata with the same set of holes in Section~\ref{sec:refinement} and generalize it to automata with a different set of holes in Section~\ref{sec:holes}.
+Section~\ref{sec:prop} is dedicated to formalize and prove basic properties of refinement in ; here we prove that refinement is a preorder and we focus on one composition property.
+In Section~\ref{sec:sota} we review related works, and Section~\ref{sec:ccl} concludes the paper.
 

### 2022-07-10 2021-Refinement/paper/refinementarticle.tex
Encore quelques fautes de grammaire, et 1 ou 2 TODOs, jusque page 6

@@
 Establishing equivalence and refinement relations between programs is an important mean for 
-verifying the correctness of programs. By establishing that the
+verifying their correctness. By establishing that the
 behaviours of a modified program simulate those of the source one,  and bisimulation relations  formalise the desired  relation between a specification and an implementation, 
@@
 %For instance \(\mbrc{\alpha \mapsto 1, \beta \mapsto 2, \gamma \mapsto 3}\) has no simple generating expression and is better represented with the finite version of first notation.
-The disjoint union on set is noted \(\uplus\).
+The disjoint union on sets is noted \(\uplus\).
 %\footnote{Depending on the context, \(\uplus\) notation either supposes that the sets are disjoint or constraints joined sets to be disjoints if several choices are possible}.
 Disjoint union is also used on maps.
-There are several ways of ensuring a union is disjoint, we will indifferently either suppose sets are disjoint or rename conflicting object (useful for variables).
+There are several ways of ensuring a union is disjoint, we will indifferently either suppose sets are disjoint or rename conflicting objects (useful for variables).
 %The disjoint union of two maps \(\varphi: I \to X\) and \(\psi: J \to Y\) with \(I \cap J = \emptyset\) is noted \(\varphi \uplus \psi\) and has the following signature \(I \uplus J \to X \cup Y\).
@@
 For \(e \in E\),
- \(\fvars{e}\) is the set of variables in  $e$that are not bound by a binder. An expression is closed if \(\fvars{e}=\emptyset\).
-The set \(\values\) denote values which is a subset of closed terms. \(\rformulas[V]\) is the set of formulas $f$ that only use variables in $V$, i.e. the formulas such that  \(\fvars{f}\subseteq V\).
+ \(\fvars{e}\) is the set of variables in  $e$ that are not bound by a binder. An expression is closed if \(\fvars{e}=\emptyset\).
+The set \(\values\) denotes values which is a subset of closed terms.
+\(\rformulas[V]\) is the set of formulas $f$ that only uses variables in $V$, i.e.
+the formulas such that  \(\fvars{f}\subseteq V\).
 The substitution in \(e \in E\) of \(x \in \fvars{e}\) by \(t \in \terms\), is denoted \(e\subst{t}{x}\), and its generalisation to the parallel substitution of variables in \(V\) by \(\psi: V \to \terms\) is denoted \(e\psubst{\psi}\).
 
- We suppose given a decidable satisfiability relation on formulas, \({\vdash} f\) is the satisfiability over closed formulas.
+ We suppose given a decidable satisfiability relation on formulas; we denote \({\vdash} f\) the satisfiability over closed formulas.
 % In practice one of our objective is to be able to use a SMT solver to reason automatically on the properties of open automata, in this case
 %\(\vdash\) can hence be interpreted as an indicator of what is given to the SMT; it separates the external logic and the logic on \(\formulas\).
-We will  use two satisfiability relations:
+We will use two variants of the satisfiability relation:
 \begin{itemize}
@@
 \subsection{Open Automata}\label{sec:def}
- Open automata (abbreviated OA) are labelled transition systems with variables  that can be used to compose other automata: they are made of transitions that are dependent of the actions of ``holes'', a composition operation consists in filling a hole with another automaton to obtain a more complete automaton.
+ Open automata (abbreviated OA) are labelled transition systems with variables  that can be used to compose other automata: they are made of transitions that are dependent on the actions of ``holes'', a composition operation consists in filling a hole with another automaton to obtain a more complex automaton.
 The variables makes the OA symbolic, and the holes allow for a partial definition of the behaviour.
@@
 When the transition set is clear from the context, it will be omitted.
-The local variables of a transition \(\fvars{t}\) are all variables appearing in transition \(t\) except the global variables of the automaton.
+The local variables of a transition \(\fvars{t}\) are all variables appearing in transition \(t\) except the variables of the automaton.
 %\begin{align*}
@@
    \includegraphics[width=.9\textwidth]{Figures/database.pdf}
-   \caption{Open Automaton. It exposes an unspecified counter in the hole
+   \caption{Open Automaton. It exposes an unspecified counter in the "cnt" hole
  to count external tick actions. The system sets a counter when a query is enabled and updates  when  the time is over.\label{Fig:SpecOA}}
@@
 OA are partially specified automata, that partiality comes  from the holes.
-A hole is a port in which we can plug an OA.
+A hole can be seen as a port in which we can plug an OA.
 The plugging operation is called composition.
@@
 The definition of composition below is a direct translation of what happens with pNets composition without  introducing pNets.
+\TODO{Beware, c'est la premiere apparition de "PNets", c'est un peu brutal...}
 
@@
 The first OA decides when the second can evolve by involving its hole in a transition:
-The action emitted when \(A_p\) makes a transition is synchronised with the action of the hole \(k\) in transitions of \(A_c\).
+the action emitted when \(A_p\) makes a transition is synchronised with the action of the hole \(k\) in transitions of \(A_c\).
 
@@
    \includegraphics[width=.3\textwidth]{Figures/compose_count_db.pdf}
-   \caption{Open Automaton of \texttt{counter} process (left).
+   \caption{(left) Open Automaton of \texttt{counter} process.
 Its role is to get a target, then count ticks until that target is reached, then emits an action with the elapsed time and restart.
-And Open Automaton of  the composition \texttt{database}[\texttt{counter/cnt}] (right).\label{Fig:counter}}
+(right) Open Automaton of the composition \texttt{database}[\texttt{counter/cnt}].\label{Fig:counter}}
 \end{figure}
@@
 Each state of the composite consists of a state of \texttt{database} together with a state of \texttt{counter}.
-The composed automaton  takes over  the same steps as the   \texttt{database} automaton but it also includes new steps,  indicting the change of states for the setting of timer.
+The composed automaton  takes over  the same steps as the   \texttt{database} automaton but it also includes new steps,  indicating the change of states for the setting of timer.
 
@@
 \end{definition}
+\TODO{C'est etrange, la formulation "the variables they refer to", comme il n'y a plus de variables d'etat...}
 The idea is that two states are related if the variables they refer to verify a certain formula.
@@
 Bisimulation between OA was defined in~\cite{fh-bisim}. Instead of recalling its definition we show below the principles of this bisimulation.
+\TODO{Je ne comprends pas cette figure... elle est incomplete ? Ou alors il faut un peu d'explications...}
 
@@
 Similarly to FH-bisimulation~\cite{fhbisim} we are interested  in finding relations between states of two open automata that contain variables and holes.
-However here we want to build a refinement relation that  also guarantees that no deadlock is introduced when refining the automaton (at least not among the scenarios originally planned in trhe specification).
+However here we want to build a refinement relation that  also guarantees that no deadlock is introduced when refining the automaton (at least not among the scenarios originally planned in the specification).
 The refinement relation should be conditioned by the internal states of the automata.
-More precisely, a refinement relation characterizes when two states are related, this  characterisation is expressed as a predicate on the variables of the two automata.
+More precisely, a refinement relation characterizes when two states are related, and this  characterisation is expressed as a predicate on the variables of the two automata.
 Thus, a refinement relation has the following signature: \( S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
@@
 
-The idea is that we rely on a classical notion of simulation inspired from~\cite{fh-bisim}.
+%The idea is that 
+We rely on a classical notion of simulation inspired from~\cite{fh-bisim}.
 The idea is that two states related by a given relation and states that if one state can do a transition, then the other can do a transition too.
-But to limit the creation of deadlock when simulating an automaton, we first define when a relation is preserved along identical transition  before characterising a first simple refinement relation  to compare automata with identical holes.
+But to limit the creation of deadlocks when simulating an automaton, we first define when a relation is preserved along identical transitions before characterising a first simple refinement relation  to compare automata with identical holes.
 

### 2022-07-11 2021-Refinement/paper/refinementarticle.tex
Suggestions de modifications

@@
 \documentclass[runningheads]{llncs}
+
+% TODO: would you like some consistency work in the notations of transitions (esp. True formula and empty map)
 
@@
 verifying their correctness. By establishing that the
-behaviours of a modified program simulate those of the source one,  and bisimulation relations  formalise the desired  relation between a specification and an implementation, 
+behaviours of a modified program simulate those of the source one, bisimulation relations formalise the desired relation between a specification and an implementation, 
  two equivalent implementations, or a program and its optimised implementation.
@@
  It is usually defined as trace inclusion or simulation  \cite{Milner:1980,Kouchnarenko:2007}; this ensures that all behaviours of the implementation must be also behaviours of the specification.
-\TODO{heu c'est pas le contraire, l'implem (le "refined"), peut avoir plus de comportements que la spec, non ?}
+\TODO{heu c'est pas le contraire, l'implem (le "refined"), peut avoir plus de comportements que la spec, non ?
++1}
  This definition, which is based on systems whose behaviour is fully defined, is not well-suited for open systems,  as it requires to reason also about unspecified behaviours.
-In this article we mostly rely on a simulation point of view, where all the specified behaviours must be followed by the refined system but additional behaviours may exist.
-\TODO{the following sentence is a copy of the previous paragraph !} However we also ensure that a whole scenario, made of several steps, of the specification can also be simulated by the refined system, which is a bit richer than the traditional simulation relation.
 
 Open automata were defined as a way to provide a semantics for open parameterized hierarchical LTSs used in verification tools.
+% TODO? This could be an opportunity to introduce pNets as they are reffered to later but not introduced
 An open automaton \cite{henrio:01299562} is a classical automaton with variables and holes.
@@
 Let \(V\) be the variable names of the considered automaton, \(T\) its transitions and \(r\) one of its states.
-\(\fOT[T]{r} \in T\) are called the out-transitions of the state \(r\).
-%\(\fIT[T]{r} \in T\) are called the in-transitions of the state \(r\).
+\(\fOT[T]{r} \subset T\) are called the out-transitions of the state \(r\).
+%\(\fIT[T]{r} \subset T\) are called the in-transitions of the state \(r\).
 When the transition set is clear from the context, it will be omitted.
@@
 \begin{definition}[Composition of open automata] \label{Def:CompOA}
+% TODO: this definition is a bit strange, why is Ac in the hole of Ap but the hole is in Ac and the notation is reversed?
 The composition of \(A_c = \OAg[c]\) in the hole \(k \in J_c\) of  \(A_p = \OAg[p]\) is the OA defined as follows:
@@
 \end{definition}
-\TODO{C'est etrange, la formulation "the variables they refer to", comme il n'y a plus de variables d'etat...}
+\TODO{C'est etrange, la formulation "the variables they refer to", comme il n'y a plus de variables d'etat... +1}
 The idea is that two states are related if the variables they refer to verify a certain formula.
-Additionally, we may check that initial states of the automata are related by checking that: \(\sigma_{01} \uplus \sigma_{022} \vdash R\mpar{s_{01}, s_{02}}\).
+Additionally, we may check that initial states of the automata are related by checking that: \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\).
 
@@
 More precisely, a refinement relation characterizes when two states are related, and this  characterisation is expressed as a predicate on the variables of the two automata.
-Thus, a refinement relation has the following signature: \( S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
+Thus, a refinement relation has the following signature: \( S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\). % TODO: duplicata avec Def Relation on OA states
 
@@
 
+% TODO: simulation doesn't introduce deadlocks, it doesn't forbid it, or tolerates it but it doesn't introduces deadlocks by itself.
 Let us first explain the reasons why simulation can introduce deadlocks and how we want too limit them. 
@@
   is preserved along identical transitions if  it satisfies the following:
+% TODO: isn't it a2 = a1x instead of a1x = a1
 \begin{multline*}
@@
 In this case, we want to ensure that the automaton with a filled hole is a refinement of the other automata: actions of the identical holes will be taken into account the same way, and filling the hole partially reduces the behaviour of the automaton.
+% TODO: what does this last part (after comma) means?
 
@@
 This way, in the example above, we would have no guarantee on actions the hole $j$ by transitivity but can state a refinement relation with guarantees on the actions of the other holes.
+% TODO: Too many "way"
 
@@
 
+% TODO: sorry, what is R? I don't understand this definition, why v = v on vars(s1), what about s2
 The relation  \(\wrel{}{}{H}\) is reflexive,  \(\wrel{A}{A}{H}\),  by taking $R\mpar{s_1, s_2} \mapsto \displaystyle\bigwedge_\subbox{v \in vars(s_1)} {v=v}$ to be $s_1= s_2$  and checking the above conditions (Definition \ref{Def:OA-Refinement}), we can see that the relation is indeed reflexive.
@@
 More precisely, we define a relation of the following form:
+% TODO: this relation defines is
   \[R_{13}(s_1,s_3)=\bigvee_{s_2\in S_2}\mpar{R_{12}(s_1,s_2) \land R_{23}(s_2,s_3) } \]
@@
 
+% TODO: why is there several ovoid stacked only on one side?
 \begin{center}
@@
 
+% TODO: non-blocking is not defines afaik
 Open automata composition is a refinement where

### 2022-07-12 2021-Refinement/paper/refinementarticle.tex
merge and resolution of many todos

@@
 Refinement entails that one system can be considered as a more precise version of the specification, featuring all the specified behaviours with more concrete details.
- It is usually defined as trace inclusion or simulation  \cite{Milner:1980,Kouchnarenko:2007}; this ensures that all behaviours of the implementation must be also behaviours of the specification.
-\TODO{heu c'est pas le contraire, l'implem (le "refined"), peut avoir plus de comportements que la spec, non ?
-+1}
+ It is usually defined as trace inclusion or simulation  \cite{Milner:1980,Kouchnarenko:2007}; this ensures that all behaviours of the specification must belong to the behaviours of the implementation .
  This definition, which is based on systems whose behaviour is fully defined, is not well-suited for open systems,  as it requires to reason also about unspecified behaviours.
 
-Open automata were defined as a way to provide a semantics for open parameterized hierarchical LTSs used in verification tools.
-% TODO? This could be an opportunity to introduce pNets as they are reffered to later but not introduced
+Open automata were defined as a way to provide a semantics for open parameterized hierarchical LTSs used in verification tools and called \emph{pNets}.
 An open automaton \cite{henrio:01299562} is a classical automaton with variables and holes.
 Variables make automata symbolic and allow them to encode infinite state systems.
-Holes enable the composition of automata: an automaton with a hole is an operator that takes another automaton as parameter and reacts to the actions it emits; the composed automaton is a more precise automaton where the behaviour of one ``parameter'' \TODO{est-ce qu'on n'ecrirait pas ici "process parameter" pour les distinguer des variables standard ?} of the main automaton has been provided.
+Holes enable the composition of automata: an automaton with a hole is an operator that takes another automaton as parameter and reacts to the actions it emits; the composed automaton is a more precise automaton where the behaviour of one ``process parameter'' % \TODO{est-ce qu'on n'ecrirait pas ici "process parameter" pour les distinguer des variables standard ?}
+% LUDO: DONE
+ of the main automaton has been provided.
 
@@
 Families of values, or equivalently maps will be noted \(x_i^{i \in I}\), \(\mset{i \mapsto x_i}{i \in I}\), or \(\mset{i \gets x_i}{i \in I}\), depending on what is more convenient.
-% TODO: introduire le fait que \exists c_j^{j \in J} défini J et {j \mapsto c_j}
+Statements like  $\exists c_j^{j \in J}$ defines both $J$ and the mapping ${j \mapsto c_j}$.
 %For instance \(\mpar{ax}^{x \in \setR}\) represents a scaling function, \(c^{i \in I}\) is a constant function over \(I\).
@@
 The plugging operation is called composition.
-The composition of OA was already implicitly defined by the means of composition on pNets in previous work \cite{henrio:01299562} but never  formalised on OA.
-The definition of composition below is a direct translation of what happens with pNets composition without  introducing pNets.
-\TODO{Beware, c'est la premiere apparition de "PNets", c'est un peu brutal...}
+The composition of OA was already implicitly defined by the means of composition on pNets in previous work \cite{henrio:01299562} but never  formalised on OA\footnote{The definition of composition below is a direct translation of what happens with pNets composition without  introducing pNets.}
 
@@
 More precisely, a refinement relation characterizes when two states are related, and this  characterisation is expressed as a predicate on the variables of the two automata.
-Thus, a refinement relation has the following signature: \( S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\). % TODO: duplicata avec Def Relation on OA states
+Thus, a refinement relation is a relation on OA states.
 
@@
 
-% TODO: simulation doesn't introduce deadlocks, it doesn't forbid it, or tolerates it but it doesn't introduces deadlocks by itself.
-Let us first explain the reasons why simulation can introduce deadlocks and how we want too limit them. 
+Let us first explain the reasons why simulation can introduce allow undesired bwhaviours to emerge and how we want to limit them. 
 The automaton that simulates a specification features any behaviour that contains the behaviour of the specification, or more precisely, for each state that simulates a state of the specification, the simulating automaton must at least feature the behaviour of the specification.
- In this definition, nothing prevents the implementation from adding non-determinism and non-deterministically reaching a state that is unrelated to the specification, this state could be a deadlock even though we only followed transitions that exist in the specification.
+ In this definition, nothing prevents the implementation from adding non-determinism and non-deterministically reaching a state that is unrelated to the specification, this state could even be a deadlock even though we only followed transitions that exist in the specification.
 To avoid the appearance of such deadlocks, we will state that, when both the implementation and the specification do the same transition, they stay related.
@@
 % TODO: isn't it a2 = a1x instead of a1x = a1
+% TODO: ANS:  we have a1 = a2 so whatever, it is the same, we can change if it is more ``natural''
 \begin{multline*}
@@
 The way we solve this issue is to remember in the simulation relation which holes have been compared.
-This way the relation is parameterized by the set of holes that belong to the two automata and are taken into account.
+This makes the relation parameterized by a subset of the set of holes that belong to the two automata that we want to take into account.
 This way, in the example above, we would have no guarantee on actions the hole $j$ by transitivity but can state a refinement relation with guarantees on the actions of the other holes.
-% TODO: Too many "way"
 
@@
 
-% TODO: non-blocking is not defines afaik
-Open automata composition is a refinement where
-the tracked holes are the holes of the base automaton minus the composed hole.
-\begin{theorem}[Composition is a refinement]\label{thm:Composition}
-Let $A_1$ and  $A_2$  be three two automata with $J_1$ the set of holes of $A_1$.
-Suppose that \(k \in J_1\) and that \(A_1\subst{A_2}{k}\) is non-blocking. We have:
-\[ \wrel{A_1\subst{A_2}{k}}{A_1}{J_1\setminus \{k\}}\]
-\end{theorem}
-
-TODO: FOCUS on the two following items (look at quentin's article):
-
-- what is the property wrt deadlocks?
-
-- relation with fh bisimulation
+%% TODO: non-blocking is not defines afaik
+%% ANS: remove this from the submission because proof unfinished
+%Open automata composition is a refinement where
+%the tracked holes are the holes of the base automaton minus the composed hole.
+%\begin{theorem}[Composition is a refinement]\label{thm:Composition}
+%Let $A_1$ and  $A_2$  be three two automata with $J_1$ the set of holes of $A_1$.
+%Suppose that \(k \in J_1\) and that \(A_1\subst{A_2}{k}\) is non-blocking. We have:
+%\[ \wrel{A_1\subst{A_2}{k}}{A_1}{J_1\setminus \{k\}}\]
+%\end{theorem}
+
+%TODO: FOCUS on the two following items (look at quentin's article):
+%
+%
+%- what is the property wrt deadlocks?
+%
+%
+%- relation with fh bisimulation
 

### 2022-07-12 2021-Refinement/paper/refinementarticle.tex
proof in progess

--- 2022-07-10 2021-Refinement/paper/refinementarticle.tex
@@
 
-Let's consider any $s_{2p} \in (s_{2p})^{p\in P}$. According to the refinement relation between  $A_1$ and $A_2$ and Definition \ref{def:preservation} we have:
+Let's consider any $s_{2p} \in (s_{2p})^{p\in P}$. According to the refinement relation between  $A_1$ and $A_2$ we have the following:
 
@@
 
-Furthermore, according to the refinement relation between  $A_2$ and $A_3$ and Definition \ref{Def:OA-Refinement} we have  for any open transition $t_{2px}$ in $T_2$ originating from $s_{2p}$ the following:
+Yet according to the refinement  relation between   $A_2$ and $A_3$ the following is satisfied:
+\begin{multline*}
+\bigforall \mpar{s_{2p}, s_3} \in S_1 \times S_3, \bigsymb{\forall} \mpar{t_{2p}, t_3} = \mpar{\OTx{2p}{}{2p}{2p}, \OTx{3}{}{3}{3}} \in \fOT{s_{2p}} \times \fOT{s_3} \\ 
+\bigsymb{\bigexists} 
+\mpar{t_{2px} = \OTx{2p}{x}{2px}{2px} \in \fOT{s_{2p}}}^{y \in Y},
+V_2 \uplus V_3\uplus \biguplus_{x\in X}\fvars{t_{2px}} \uplus \fvars{t_3} \uplus \fvars{t_{2p}} \vdash \hspace{6cm}\\  R_{23}\mpar{s_2, s_3} \wedge 	g_{2p}\wedge g_3 \wedge \alpha_2 = \alpha_3 
+%\wedge \bigwedge_\subbox{j \in J'_2 \cap J'_3} \beta_{2pj} = \beta_{3j} 
+\implies \hspace{6cm}\\
+%\exists
+%\OTx{1}{a}{3}{3}\in \fOT{s_2}. \\
+\bigsymb{\bigwedge_{x\in X}}
+\mpar{
+\alpha_{2p}=\alpha_{2p x}  \land J'_{2px}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{2xj}\land g_{2p x}\land
+ R_{23}\mpar{s'_{2p x}, s'_3}\psubst{\psi_{2p x} \uplus \psi_3}}\\
+\end{multline*}
+
+For any open transition $t_{2px}$ originating from $s_{2p}$ we have 
+the following by definition of refinement between  $A_2$ and $A_3$:
+
 \begin{align*}
@@
 \begin{align*}
-\mpar{\OTx{3}{py}{3py}{3py} \in \fOT{s_3}}^{y \in Y} 
-\end{align*}
-such that $\forall y \in Y, J'_{2p} \cap H = J'_{3py} \cap H$ and
+\mpar{\OTx{3}{pxy}{3pxy}{3pxy} \in \fOT{s_3}}^{y \in Y} 
+\end{align*}
+such that $\forall y \in Y, J'_{2px} \cap H = J'_{3py} \cap H$ and
 \begin{multline*}
 %\everymath{\displaystyle}
-V_2 \uplus V_3 \uplus \fvars{t_{2p}} \vdash\\
-R_{23}\mpar{s_{2p}, s_{3}} \wedge g_{2p} \implies  \operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			 \alpha_{2p}=\alpha_{3py} \wedge \bigwedge_\subbox{j \in J'_{3py} \cap H} \beta_{2pj}=\beta_{3pyj} \nwedge \\
-			g_{3py} \wedge R_{23}\mpar{s'_{2p}, s'_{3y}}\psubst{\psi_{2p} \uplus \psi_{3py}}
+V_2 \uplus V_3 \uplus \fvars{t_{2px}} \vdash\\
+R_{23}\mpar{s_{2p}, s_{3}} \wedge g_{2px} \implies  \operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			 \alpha_{2px}=\alpha_{3pxy} \wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H} \beta_{2pxj}=\beta_{3pxyj} \nwedge \\
+			g_{3pxy} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
 		\end{array}}  

### 2022-07-13 2021-Refinement/paper/refinementarticle.tex
Def 3
solved some todos

--- 2022-07-12 2021-Refinement/paper/refinementarticle.tex
@@
 The plugging operation is called composition.
-The composition of OA was already implicitly defined by the means of composition on pNets in previous work \cite{henrio:01299562} but never  formalised on OA\footnote{The definition of composition below is a direct translation of what happens with pNets composition without  introducing pNets.}
+The composition of OA was already implicitly defined by the means of composition on pNets in previous work \cite{henrio:01299562} but never  formalised on OA\footnote{The definition of composition below is a direct translation of what happens with pNets composition \cite{henrio:01299562} without  introducing pNets.}
 
@@
 \section{A Refinement Relation that Takes Holes into Account}\label{sec:holes}
-\TODO{3.5 pages}
 
@@
 A simple use-case for this is filling a hole with a completely defined automaton.
-In this case, we want to ensure that the automaton with a filled hole is a refinement of the other automata: actions of the identical holes will be taken into account the same way, and filling the hole partially reduces the behaviour of the automaton.
-% TODO: what does this last part (after comma) means?
+In this case, we want to ensure that the automaton with a filled hole is a refinement of the other automata: actions of the identical holes will be taken into account the same way.
 
@@
 
-% TODO: sorry, what is R? I don't understand this definition, why v = v on vars(s1), what about s2
-The relation  \(\wrel{}{}{H}\) is reflexive,  \(\wrel{A}{A}{H}\),  by taking $R\mpar{s_1, s_2} \mapsto \displaystyle\bigwedge_\subbox{v \in vars(s_1)} {v=v}$ to be $s_1= s_2$  and checking the above conditions (Definition \ref{Def:OA-Refinement}), we can see that the relation is indeed reflexive.
+% TODO: I don't understand this definition, why v = v on vars(s1), what about s2
+% ANS: was copy paste from the report, polished now
+The relation  \(\wrel{}{}{H}\) is reflexive,  \(\wrel{A}{A}{H}\).
+This is shown  by considering the relation $R$ such that $R\mpar{s_1, s_2} \triangleq s_1=s_2\land \displaystyle\bigwedge_\subbox{v \in vars(s_1)} {v=v}$   we can prove the conditions for Definition~\ref{Def:OA-Refinement}.
 %
@@
 
-The next two theorems state that refinement is compositional in the sense that it is sufficient to prove refinement for the composed automata separately to obtain a refinement relation.
-This can be split into theorems that can be trivially composed by transitivity.
+The next  theorem states that if two automata are in refinement relation and the same automata is placed in the same hole of the two autaomata, then the refinement is rpreserved.
+This is the first step toward proving that
+ refinement is compositional in the sense that it is sufficient to prove refinement for the composed automata separately to obtain a refinement relation.
+The second part, i.e. proving that placing in the same context two OA in refinement, we obtain two OA in refinement is left for future works.
 %
@@
 
-\begin{theorem}[Congruence]\label{thm:Congruence}
-Let $A_1$, $A_2$ and $A_3$ be three open automata with $\wrel{A_2}{A_3}{H}$. 
-%Suppose that \(k \in H\) and that \(A_1\subst{A_2}{k}\) is non-blocking.
-We have: \[\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{J_1 \uplus H \setminus \mbrc{k}}\]
-\end{theorem}
+%
+%
+%
+%
+%\begin{theorem}[Congruence]\label{thm:Congruence}
+%Let $A_1$, $A_2$ and $A_3$ be three open automata with $\wrel{A_2}{A_3}{H}$. 
+%%Suppose that \(k \in H\) and that \(A_1\subst{A_2}{k}\) is non-blocking.
+%We have: \[\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{J_1 \uplus H \setminus \mbrc{k}}\]
+%\end{theorem}
 

### 2022-07-13 2021-Refinement/paper/refinementarticle.tex

@@
 % TODO: this definition is a bit strange, why is Ac in the hole of Ap but the hole is in Ac and the notation is reversed?
-The composition of \(A_c = \OAg[c]\) in the hole \(k \in J_c\) of  \(A_p = \OAg[p]\) is the OA defined as follows:
+The composition of \(A_p = \OAg[p]\) in the hole \(k \in J_c\) of    \(A_c = \OAg[c]\) is the OA defined as follows:
 \[A_c\subst{A_p}{k} ::=  \OA{S_c \times S_p}{\mpar{s_{0c}, s_{0p}}}{V_c \uplus V_p}{\sigma_{0c} \uplus \sigma_{0p}}{J_p \uplus J_c \setminus \mbrc{k}}{T} \] \text{with }

### 2022-07-13 2021-Refinement/paper/refinementarticle.tex
typos + comment under Def 6

@@
 Refinement entails that one system can be considered as a more precise version of the specification, featuring all the specified behaviours with more concrete details.
- It is usually defined as trace inclusion or simulation  \cite{Milner:1980,Kouchnarenko:2007}; this ensures that all behaviours of the specification must belong to the behaviours of the implementation .
+ It is usually defined as trace inclusion or simulation  \cite{Milner:1980,Kouchnarenko:2007}; this ensures that all behaviours of the specification must belong to the behaviours of the implementation.
  This definition, which is based on systems whose behaviour is fully defined, is not well-suited for open systems,  as it requires to reason also about unspecified behaviours.
@@
 Suppose an identical transition exist in both automata (with same guards and same label), then either the reached states $s_1'$ and $s_2'$ are related by refinement, or there exists another transition of the specification that is also identical and leads to a state $s_1''$ that is related to $s_2'$ in the refinement relation.
-Finally, we should take into account that 1) instead of equality, we should check if there is a state such that both transitions are feasible (the conjunction of guards is satisfiable), and that  2)instead of finding another transition of the specification we might find a family of transitions that cover all the cases of the transition of the implementation.
+Finally, we should take into account that 1) instead of equality, we should check if there is a state such that both transitions are feasible (the conjunction of guards is satisfiable), and that  2) instead of finding another transition of the specification we might find a family of transitions that cover all the cases of the transition of the implementation.
 This leads us to the following definition.
@@
 %Note also the second part of the conjunction of condition (2) expresses the deadlock reduction between automata (as introduced in Definition \ref{def:dpwd}).
+\TODO{The first and second conditions coincide with the natural way to prove inductively that an automaton simulates another by starting with the initial state.
+The third condition ensures that the refinement relation does prevent the introduction of deadlocks.}
 
@@
 \end{multline*}
-
 For any open transition $t_{2px}$ originating from $s_{2p}$ we have 

### 2022-07-13 2021-Refinement/paper/refinementarticle.tex
typos + comment under Def 6
todos

--- 2022-07-13 2021-Refinement/paper/refinementarticle.tex
@@
 \TODO{C'est etrange, la formulation "the variables they refer to", comme il n'y a plus de variables d'etat... +1}
-The idea is that two states are related if the variables they refer to verify a certain formula.
+The idea is that two states are related depending on the state of the automaton, i.e. if the variables of the OA verify a certain formula. 
+In other words, for each pair of states, a boolean formula that may refer to the  variables of each of the two OA states whether the two states are related or not.
 Additionally, we may check that initial states of the automata are related by checking that: \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\).
@@
 \section{Properties of our Refinement Relations}\label{sec:prop}
-\TODO{1.5 pages}
+
 We now  state the properties of our refinement relations, proofs of the properties can be found in the appendices.
@@
 
-\TODO{i did not put the global composition theorem, de we state it?}
+%\TODO{i did not put the global composition theorem, de we state it?}
 

### 2022-07-13 2021-Refinement/paper/refinementarticle.tex

--- 2022-07-13 2021-Refinement/paper/refinementarticle.tex
@@
 \TODO{The first and second conditions coincide with the natural way to prove inductively that an automaton simulates another by starting with the initial state.
-The third condition ensures that the refinement relation does prevent the introduction of deadlocks.}
+The third condition ensures that the refinement relation prevents the introduction of deadlocks.}
 

### 2022-07-13 2021-Refinement/paper/refinementarticle.tex
meeting notes

@@
 \section{Introduction}
+
+\TODO{Entete : rabea}
+
+\TODO{explication bisim: Ludo}
 
@@
 This section presents our notations and the principles of automata.
-Except for minor changes in the notations, compared to previous works~\cite{pnets} the only new contribution is the definition of a composition operator for open automata.
+Except for minor changes in the notations, compared to previous works~\cite{fhbisim} the only new contribution is the definition of a composition operator for open automata.
 %
@@
 \end{definition}
+
+We use two operators to access pieces of information of the OA.
 
@@
 
-\paragraph{Open automaton composition}
+\paragraph{Open automaton composition.}
 
@@
 \end{definition}
-\TODO{C'est etrange, la formulation "the variables they refer to", comme il n'y a plus de variables d'etat... +1}
+%\TODO{C'est etrange, la formulation "the variables they refer to", comme il n'y a plus de variables d'etat... +1}
 The idea is that two states are related depending on the state of the automaton, i.e. if the variables of the OA verify a certain formula. 
@@
 
-\paragraph{A bisimulation for open automata}
-
-Bisimulation between OA was defined in~\cite{fh-bisim}. Instead of recalling its definition we show below the principles of this bisimulation.
+\paragraph{A bisimulation for open automata.}
+
+Bisimulation between OA was defined in~\cite{fhbisim}. Instead of recalling its definition we show below the principles of this bisimulation.
 \TODO{Je ne comprends pas cette figure... elle est incomplete ? Ou alors il faut un peu d'explications...}
@@
 %The idea is that 
-We rely on a classical notion of simulation inspired from~\cite{fh-bisim}.
+We rely on a classical notion of simulation inspired from~\cite{fhbisim}.
 The idea is that two states related by a given relation and states that if one state can do a transition, then the other can do a transition too.
@@
 
-\medskip
-
-We define here simulation between labelled transition systems to Hole-equal simulation  between  open automata that have exactly the same holes.
+\TODO{[LUDO]
+We define here simulation between labelled transition systems to Hole-equal simulation  between  open automata that have exactly the same holes. }
 \begin{definition}[Hole-equal simulation]
@@
 %Note also the second part of the conjunction of condition (2) expresses the deadlock reduction between automata (as introduced in Definition \ref{def:dpwd}).
-\TODO{The first and second conditions coincide with the natural way to prove inductively that an automaton simulates another by starting with the initial state.
-The third condition ensures that the refinement relation prevents the introduction of deadlocks.}
+The first and second conditions coincide with the natural way to prove inductively that an automaton simulates another by starting with the initial state.
+The third condition ensures that the refinement relation prevents the introduction of deadlocks.
 
@@
 
-\begin{figure}[h]
+\begin{figure}[!tb]
  \centering
@@
 
-\TODO{The refinement relation  also specifies that the refined process must follow the behaviour of the specification, not only at every compatible state but also along any trace.}
-
- We will show in Section~\ref{sec:prop} that this refinement relation has good properties in terms of transitivity, compositionality, reflexivity, etc.
+The refinement relation  also specifies that the refined process must follow the behaviour of the specification, not only at every compatible state but also along any scenario of the specification.
+We will show in Section~\ref{sec:prop} that this refinement relation has good properties in terms of transitivity, compositionality, and reflexivity.
 
@@
 %Technically,  it expresses how the concepts from the abstract and the refined systems are linked together.
-
-\TODO{add an example}
 
@@
 
+\TODO{[LUDO] relire et virer le rouge}
 This definition leads to a notion of simulation as refinement the same as the one used in LOTOS \cite{Brinksma:87} and presented under the name extension refinement.
@@
 \end{lemma}
-\TODO{example}
 
@@
 
+\TODO{[RABEA] figure}
 \begin{center}
@@
 
+\TODO{[LUDO] proof sketch}
+
+\TODO{[RABEA] example : composition and refinement}
+
 % TODO: why is there several ovoid stacked only on one side?
-\begin{center}
-\includegraphics[scale=0.7]{Figures/Theorem1}
-\end{center}
+%\begin{center}
+%\includegraphics[scale=0.7]{Figures/Theorem1}
+%\end{center}
 
@@
 
-\TODO{1 page}
+\TODO{[RABEA] RW}
 
@@
 \end{align*}
-\item Second, we need to prove for any OT $t_{13}$ in $T_{13}$ originating from $s_{13}$:
+\item Second, we need to prove for any open transition $t_{13}$ in $T_{13}$ originating from $s_{13}$:
 \begin{align*}
@@
 
-We reason on the way the OT $t_{23}$ has been obtained: either the hole $k$ of $A_2$ is involved in the transition or not.
+We reason on the way the open transition $t_{23}$ has been obtained: either the hole $k$ of $A_2$ is involved in the transition or not.
 
@@
 
-\item Second, we need to prove for any OT $t_{12}$ in $T_{12}$ originating from $s_{12}$
+\item Second, we need to prove for any open transition $t_{12}$ in $T_{12}$ originating from $s_{12}$
 
@@
 
-We reason on the way the OT $t_{13}$ has been obtained: either the hole $k$ of $A_1$ is involved in the transition or not.
+We reason on the way the open transition $t_{13}$ has been obtained: either the hole $k$ of $A_1$ is involved in the transition or not.
 

### 2022-07-13 2021-Refinement/paper/refinementarticle.tex
meeting notes
meeting notes + rel on config

@@
 \[A_c\subst{A_p}{k} ::=  \OA{S_c \times S_p}{\mpar{s_{0c}, s_{0p}}}{V_c \uplus V_p}{\sigma_{0c} \uplus \sigma_{0p}}{J_p \uplus J_c \setminus \mbrc{k}}{T} \] \text{with }
-
-\begin{align*}
-T=& \mset{\OT{\mpar{s_c, s_p}}{\mpar{s'_c, s'_p}}{\alpha_c}{\beta_j^{j \in J'_p \uplus J'_c}}{g_c \wedge g_p \wedge \alpha_p = \beta_k}{\psi_c \uplus \psi_p}}{ \OT{s_c}{s'_c}{\alpha_c}{\beta_j^{j \in J'_c \uplus \mbrc{k} }}{g_c}{\psi_c} \in T_c, \OTx{p}{}{}{p} \in T_p} \\
+\begin{align*}
+T\!=& \mset{\OT{\mpar{s_c, s_p}}{\mpar{s'_c, s'_p}}{\alpha_c}{\beta_j^{j \in J'_p \uplus J'_c}\!}{g_c \wedge g_p \wedge \alpha_p = \beta_k}{\psi_c \uplus \psi_p}}{ \OT{s_c}{s'_c}{\alpha_c}{\beta_j^{j \in J'_c \uplus \mbrc{k} }\!}{g_c}{\psi_c} \in\!
+T_c, \OTx{p}{}{}{p} \in\!
+T_p} \\
 	& \cup \mset{\OT{\mpar{s_c, s_p}}{\mpar{s'_c, s_p}}{\alpha_c}{\beta_j^{j \in J'_c}}{g_c}{\psi_c}}{\OTx{c}{}{}{c} \in T_c, k \notin J'_c, s_p \in S_p}
@@
 To do so we will suppose that the variables of the two OA are disjoint (a renaming of variables may have to be applied before comparing OA states).
-\begin{definition}[Relation on OA states] Suppose $V_1$ and $V_2$ are disjoint.
-A relation on states of \(\OAg[1]\) and \(\OAg[2]\) is a function \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
+\begin{definition}[Relation on OA configurations] Suppose $V_1$ and $V_2$ are disjoint.
+A relation on configurations of \(\OAg[1]\) and \(\OAg[2]\) is a function \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
 \end{definition}
@@
 
-Similarly to FH-bisimulation~\cite{fhbisim} we are interested  in finding relations between states of two open automata that contain variables and holes.
+Similarly to FH-bisimulation~\cite{fhbisim} we are interested  in finding relations between configurations of two open automata that contain variables and holes.
 However here we want to build a refinement relation that  also guarantees that no deadlock is introduced when refining the automaton (at least not among the scenarios originally planned in the specification).
@@
 More precisely, a refinement relation characterizes when two states are related, and this  characterisation is expressed as a predicate on the variables of the two automata.
-Thus, a refinement relation is a relation on OA states.
+Thus, a refinement relation is a relation on OA configurations.
 
@@
 We rely on a classical notion of simulation inspired from~\cite{fhbisim}.
-The idea is that two states related by a given relation and states that if one state can do a transition, then the other can do a transition too.
+The idea is that two configurations related by a relation; if one state can do a transition, then the other can do a transition too.
 But to limit the creation of deadlocks when simulating an automaton, we first define when a relation is preserved along identical transitions before characterising a first simple refinement relation  to compare automata with identical holes.
@@
 \bigsymb{\bigexists} 
-\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},
- V_1 \uplus V_2 \uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_2} \uplus \fvars{t_1} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 
+\mpar{t_{1x} \!=\! \OTx{1}{x}{1x}{1x} \!\in\! \fOT{s_1}}^{x \in X}\!,
+ V_1 \uplus V_2 \uplus \biguplus_{x\in X}\!\fvars{t_{1x}} \uplus \fvars{t_2} \uplus \fvars{t_1} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 
 %\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} 
@@
 \begin{definition}[Open automata refinement]\label{Def:OA-Refinement}
-For two open automata\\ \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a refinement of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a relation $R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that:
+For two open automata\\ \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a refinement of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a relation on configurations $R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that:
 \item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
@@
 More precisely, we define a relation of the following form:
-% TODO: this relation defines is
   \[R_{13}(s_1,s_3)=\bigvee_{s_2\in S_2}\mpar{R_{12}(s_1,s_2) \land R_{23}(s_2,s_3) } \]
-We then prove that this relation defines is a refinement, according to Definition~\ref{Def:OA-Refinement}.
+We then prove that this relation  is a refinement, according to Definition~\ref{Def:OA-Refinement}.
 
@@
 \TODO{[LUDO] proof sketch}
+
+\TODO{The subtlety here is that the original relation implies that valuations in A3 are equal (ie the value for each variable are the same in both valuations, modulo renaming), after a transition we should obtain ``equal'' valuations because Post are deterministic}
 
@@
 
+\TODO{[RABEA] proof}
 Let's consider any $s_{2p} \in (s_{2p})^{p\in P}$. According to the refinement relation between  $A_1$ and $A_2$ we have the following:
@@
 \end{quote}
-
-\TODO{The subtlety here is that the original relation implies that valuations in A3 are equal (ie the value for each variable are the same in both valuations, modulo renaming), after a transition we should obtain ``equal'' valuations because Post are deterministic}
 

### 2022-07-13 2021-Refinement/paper/refinementarticle.tex
add affiliations + typos

@@
 \author{
-Rabéa\inst{1}\orcidID{1111-2222-3333-4444} \and
-Quentin\inst{1,2}\orcidID{1111-2222-3333-4444} \and
-Ludo\inst{2}\orcidID{0000-1111-2222-3333} \and
-Eric\inst{3}\orcidID{2222--3333-4444-5555}}
+Rabéa Ameur-Boulifa\inst{1}\orcidID{0000-0002-2471-8012} \and
+Quentin Corradi\inst{2}\orcidID{} \and
+Ludovic Henrio \inst{2}\orcidID{0000-0001-7137-3523} \and
+Eric Madelaine \inst{3}\orcidID{0000-0002-5552-5993}}
 %
@@
 %
-\institute{blabla
-\email{lncs@fff}\\
-\url{http://www.springer.com/gp/computer-science/lncs} \and
-blibli\\
-\email{\{abc,def\}@fff}}
+\institute{LTCI, T\'el\'ecom Paris, Institut Polytechnique de Paris, France
+\email{first.last@telecom-paris.fr}\\
+\and
+Universit\'e Lyon, EnsL, UCBL, CNRS, Inria,  LIP France\\
+\email{first.last@ens-lyon.fr}
+ \and
+INRIA Sophia Antipolis M\'edit\'erann\'ee, UCA,  Sophia Antipolis, France
+\email{first.last@inria.fr}}
 %
@@
    \includegraphics[width=.3\textwidth]{Figures/compose_count_db.pdf}
-   \caption{(left) Open Automaton of \texttt{counter} process.
+   \caption{(Left) Open Automaton of \texttt{counter} process.
 Its role is to get a target, then count ticks until that target is reached, then emits an action with the elapsed time and restart.
-(right) Open Automaton of the composition \texttt{database}[\texttt{counter/cnt}].\label{Fig:counter}}
+(Right) Open Automaton of the composition \texttt{database}[\texttt{counter/cnt}].\label{Fig:counter}}
 \end{figure}
@@
 
-\paragraph{Relations between open automata}
+\paragraph{Relations between open automata.}
 A relation (bisimulation, refinement, etc.) between OA requires to compare their states.
@@
 
-Let us first explain the reasons why simulation can introduce allow undesired bwhaviours to emerge and how we want to limit them. 
+Let us first explain the reasons why simulation can introduce allow undesired behaviours to emerge and how we want to limit them. 
 The automaton that simulates a specification features any behaviour that contains the behaviour of the specification, or more precisely, for each state that simulates a state of the specification, the simulating automaton must at least feature the behaviour of the specification.
@@
 With such a relation we are able to check the refinement between two open automata with the same level of abstraction but specified differently, for example, by duplicating states, removing transitions,  reinforcing  guards, modifying variables.
-
+\begin{example} 
 To illustrate the refinement simulation of open automata, consider a variation on the \texttt{database} automaton of Fig.
@@
 We suppose that on more concrete level, in addition to querying and updating the data base,  a backup copy of it may also be made.
-
+\end{example}
 \begin{figure}[!tb]
@@
 
-The next  theorem states that if two automata are in refinement relation and the same automata is placed in the same hole of the two autaomata, then the refinement is rpreserved.
+The next  theorem states that if two automata are in refinement relation and the same automata is placed in the same hole of the two automata, then the refinement is preserved.
 This is the first step toward proving that
@@
 
-\TODO{[RABEA] figure}
 \begin{center}
-\includegraphics[scale=0.7]{Figures/Theorem2bis}
+\includegraphics[scale=0.7]{Figures/Thm2intuition}
 \end{center}
@@
 %When we will introduce refinements in Section \ref{sec:prelref}, setting an undefined variable will be considered a valid refinement, for instance a \(5\) bits register is a particular \(n\) bits register.
+
+\newpage
 

### 2022-07-13 2021-Refinement/paper/refinementarticle.tex
explain bisim

--- 2022-07-13 2021-Refinement/paper/refinementarticle.tex
@@
 \TODO{Entete : rabea}
-
-\TODO{explication bisim: Ludo}
 
@@
 
-\paragraph{Relations between open automata}
+\subsection{Relations between open automata}
 A relation (bisimulation, refinement, etc.) between OA requires to compare their states.
@@
 
-\paragraph{A bisimulation for open automata.}
-
-Bisimulation between OA was defined in~\cite{fhbisim}. Instead of recalling its definition we show below the principles of this bisimulation.
-\TODO{Je ne comprends pas cette figure... elle est incomplete ? Ou alors il faut un peu d'explications...}
-
+\subsection{A bisimulation for open automata.}
+
+Bisimulation between OA was defined in~\cite{fhbisim}.  We show below the principles of this bisimulation. We first recall the usual definition of bisimulation.
+Bisimulation can  be defined as follows for standard transition systems:
+
+\begin{definition}[Classical Bisimulation]
+  A bisimulation is a relation $\mathcal{R}$ such that $s~\mathcal{R}~t$:\\
+  \begin{minipage}[c]{.6\textwidth}
+    \[
+      \forall l~s',~ {s}\xrightarrow{l}{s'}
+      \implies
+      \exists t'.~ s' ~\mathcal{R}~ t'
+      \land {t}\xrightarrow{l}{t'}
+    \]
+    \begin{center}
+      and conversely
+    \end{center}
+    \vspace{-1ex}
+    \[
+      \forall l~t',~ {t}\xrightarrow{l}{t'}
+      \implies
+      \exists s'.~ s' ~\mathcal{R}~ t'
+      \land {s}\xrightarrow{l}{s'}
+    \]
+    \vspace{.5ex}
+  \end{minipage}
+  i.e. \qquad
+  \begin{minipage}[c]{.35\textwidth}
     \begin{tikzpicture}
+      \node (s) at (-1,1) {$s$};
+      \node (R) at (0,1) {$~\mathcal{R}$};
+      \node (t) at (1,1) {$t$};
+      \node (sp) at (-1,0) {$s^\prime$}
+      edge [<-] node[auto] {$l$} (s);
+      \node (Rp) at (0,0) {$\mathcal{R}$};
+      \node (tp) at (1,0) {$t^\prime$}
+      edge [<-] node[auto,swap] {$l$} (t);
+    \end{tikzpicture}
+  \end{minipage}
+$s$ and $t$ are bisimilar, written $s\tilde t$ iff there is a bisimulation relation $R$ sucht that  $s ~\mathcal{R}~ t$
+\end{definition}
+
+A  bisimulation relation  relates pair of states and ensures that any behaviour of one automaton can be performed by the other one while staying in relation.
+We informally explain here the symbolic nature of the bisimulation and the related complexity of its definition.
+The presence of holes in fact raises no strong difficulty here.
+Consider the two following simple OA.
+
+\noindent~\begin{tikzpicture}
   \node[state,inner sep=5pt,minimum size=10pt] (1) {$s$};
-  \node[state,inner sep=5pt,minimum size=10pt, below right of=1,right=80pt] (2) {$t$};
-  \node[state,inner sep=5pt,minimum size=10pt, above right of=1,right=80pt] (3) {$t'$};
+  \node[state,inner sep=5pt,minimum size=10pt, below right of=1,right=90pt] (2) {$t$};
+  \node[state,inner sep=5pt,minimum size=10pt, above right of=1,right=90pt] (3) {$t'$};
 
@@
 \end{tikzpicture}
+\hfill
 \begin{tikzpicture}
@@
 
-  \draw (1) edge[align=center] node[below]{\OT{}{}{\alpha(x)}{h\mapsto\beta(x)}{x<0}{y\leftarrow -x}}  (2);
-  \draw (1) edge[align=center] node[above]{\OT{}{}{\alpha(x)}{h\mapsto\beta(x)}{x\geq 0}{y\leftarrow x}} (3);
-\end{tikzpicture}
+  \draw (1) edge[align=center] node[below]{\OT{}{}{\alpha(x)}{h\mapsto\beta(x)}{tt}{z\leftarrow x}}  (2);
+%  \draw (1) edge[align=center] node[above]{\OT{}{}{\alpha(x)}{h\mapsto\beta(x)}{x\geq 0}{y\leftarrow x}} (3);
+\end{tikzpicture}~
+
+We would like these two OA to be considered bisimilar. Both can input any $\beta(x)$ input on their hole and stores the value of $x$, emitting $\alpha(x)$ along the transition.
+The different is the way $x$ is stored.
+We can then define a configuration relation $R$ such that $R(s,s_2)$ is true and $R(t,t_2)$ holds when $z\geq 0$ and $y=z$, while $R(t',t_2)$ holds when $z< 0$ and $y=-z$.
+This illustrates relation on configuration, but also allows us to realise that bisimulation is a bit more complex than in the classical case.
+Indeed, we need two transitions on the left OA to simulate a single transition on the right one.
+We should check that these two transitions cover all the cases accepted by te right hand side OA, and of course that destination states are in relation.
+Formally, fh-bisimulation is defined \cite{fhbisim} as follows
+
+ \begin{definition}[Strong FH-bisimulation]\label{def-FH-bisim} ~\\
+\noindent
+	Suppose  $\OAg[1]$ and $\OAg[2]$
+%   $A_1 = \mylangle J,\mathcal{S}_1, s_0,V_1,
+%   \mathcal{T}_1 \myrangle$ and $A_2 = \mylangle J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2 \myrangle$
+   are open automata with identical holes of the same sort, with disjoint sets of variables ($V_1\cap V_2=\emptyset$).
+
+ Then 
+$\mathcal{R}$, a relation on configurations of OAs, is an FH-bisimulation if and only if for any  states
+$s\in{S}_1$ and $t\in{S}_2$, we 
+have
+the following:
+
+ \begin{itemize}
+ \item   
+For any open transition $OT$ in ${T}_1$:
+$
+     \OTbase{s \xrightarrow{\alpha} s'}
+         {
+           \beta_j^{j\in J'}}{g_{OT}}{\psi_{OT}}
+$
+ there exists an indexed set of  open transitions $OT_x^{x\in X} \subseteq {T}_2$:
+$
+%    \left( fresh \ \set{\alpha_i}, \set{b_j}, v_x.\ \
+    \OTbase{t \xrightarrow{\alpha_x} t_x}
+         {
+           \beta_{j x}^{j\in J_{x}}}{ g_{OT_x}}{\psi_{OT_x}}   
+%         \right)
+$
+%\end{minipage}
+%\hspace{2mm}
+%\begin{minipage}{0.35\linewidth}
+%\vspace{-2em}
+%{	\includegraphics[width=1.02\linewidth]{XFIG/Bisim}}
+%\end{minipage}
+ such that  $\forall x.\, J'=J_{x}$ and there exists $Pred_{s',t_x}$ such that $(s',t_x|Pred_{s',t_x})\in 
+ \mathcal{R}$
+ and  
+\begin{multline*}
+ \mathcal{R}(s,t) \land g_{OT}\implies\\
+ \displaystyle{\bigvee_{x\in X}
+   \left( \forall j. \beta_j=\beta_{jx}  \land g_{OT_x}
+     \land \alpha\!=\!\alpha_x \land  
+     \mathcal{R}\left(s',t_x{\psi_{OT}\!\uplus\!\psi_{OT_x}}\right)\right)}
+\end{multline*}
+     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
+     %     \right)$.
+%\bigskip
+%
+% $\Pred_{s,t} \land \Pred_{OT}\implies\bigvee_{x\in X} \Pred_x$
+%and\\
+%%\hspace{1cm}
+% $ \forall{x\in X}. \Pred_x \land \Pred_{s,t} \land \Pred_{OT} \Rightarrow
+%   \left( \forall j. \beta_j=\beta_{jx}  \land \Pred_{OT_x}
+%     \land \alpha\!=\!\alpha_x \land  
+%     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\Post_{OT_x}}\right)$
+%     %     \symb{Subst}(\Pred_{target_x}, \Post_{OT} o \Post_{OT_x})
+%     %     \right)$.
+
+%     \TODO{Eric: j'ai ajoute $\exists$ sur les predicats $\Pred_{s',t_x}$, qui n'etaient pas definis...}
+
+ \item  and symmetrically any open transition from $t$ in ${T}_2$ can be 
+      covered by a set of transitions from $s$ in ${T}_1$.
+ \end{itemize}
+
+% \TODO{Eric: il reste des petits bugs genre $s^{2'}_x$ plutot que
+%   $s^{2}_x$}
+
+%Where $\symb{Subst}(\Pred,\Post)$ is the parallel substitution of all
+%assigned variables.
+
+% \TODO{do we want formulas for this?}
+ \end{definition}
 
@@
 
-\TODO{[LUDO]
-We define here simulation between labelled transition systems to Hole-equal simulation  between  open automata that have exactly the same holes. }
+We define now a simulation between OA that have the same set of holes.
+This relation thus focuses on the simulation of transitions and uses the previous definition to prevent the refined automaton from nondeterministically reaching states that introduce deadlocks in a scenario planned without deadlock in the specification.
 \begin{definition}[Hole-equal simulation]
-Consider two OAs \(\OAg[1]\) and \(\OAg[2]\) with  \(J_1 = J_2\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $S_1$ to $S_2$ if the following conditions hold:
+Consider two OA with identical set of holes:  \(\OAg[1]\) and \(\OAg[2]\) where  \(J_1 = J_2\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $S_1$ to $S_2$ if the following conditions hold:
 \item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
@@
 
+The principle of the third requirement is that the relation allows new behaviour to be added in terms of new traces, but doesn't allow new deadlocks to
+be added, i.e., for every ``path'' of the specification (abstract automaton) the implementation (refined automaton) must not add deadlocks.
+
+This definition leads to a notion of simulation as refinement similar to the one used in LOTOS \cite{Brinksma:87} and called ``extension refinement''.
+The extension consists in adding new functionalities by preserving existing ones.
+In the context of LOTOS, a functionality is roughly an acceptable trace.
+In this context, the authors define refusal of the trace and constraint refinement so that there is no more refused trace in the refined system than in the original one.
+Slightly more formally, consider an automaton with transitions $s_0 \xrightarrowdbl{t}$, consider $\mathcal{T}_A$ the set of traces of an automaton $A$; one can define the refusal of a trace $t$ as a set of actions such that all actions in the set can be refused after the automaton $A$ has performed the steps in the trace $t$, more precisely $X$ is a refusal of a trace if $\exists s.
+s_0  \xrightarrowdbl{t} s \wedge \forall a \in X.
+s \not{\xrightarrow{a}}$.
+
+Considering an OA with no  hole and no guard, i.e., in case the definitions of open automata coincide with those of automata, the fact that $R$ is preserved along identical traces ensures that the set  of refusal of valid traces is smaller in the refined automaton than in the specification.
+
 To illustrate the refinement simulation of open automata, consider a variation on the \texttt{database} automaton of Fig.
@@
 
-\TODO{[LUDO] relire et virer le rouge}
-This definition leads to a notion of simulation as refinement the same as the one used in LOTOS \cite{Brinksma:87} and presented under the name extension refinement.
-The extension consists in adding new functionalities by preserving existing ones.
-Indeed, in case there is no hole and no guard, i.e., in case the definitions of open automata coincide with those of automata, the relation allows new behaviour to be added in terms of new traces, but doesn't allow new deadlocks to
-be added, i.e., for traces of the specification (abstract automaton) the implementation (refined automaton) must not add
-deadlocks.
-
-\TODO{
-A string $t \in \mathcal{A}^*$ is a trace of an automaton if there is some state $s$ such that $s_0 \xrightarrowdbl{t}  s$. We denote the set of traces of an automaton $A$ by $\mathcal{T}_A$. \\
-Notion of Extension refinement. May be we need to introduce the notion of  refusal of
-a trace $t \in \mathcal{T}_A$ is a set of actions such that all actions in the set can be refused after the automaton $A$
-has executed the trace $t$.
+%
+%\TODO{
+%A string $t \in \mathcal{A}^*$ is a trace of an automaton if there is some state $s$ such that $s_0 \xrightarrowdbl{t}  s$. We denote the set of traces of an automaton $A$ by $\mathcal{T}_A$. \\
+%Notion of Extension refinement. May be we need to introduce the notion of  refusal of
+%a trace $t \in \mathcal{T}_A$ is a set of actions such that all actions in the set can be refused after the automaton $A$
+%has executed the trace $t$.
 \[X \in \bot_{A}(t) \Leftrightarrow \{\exists s.
@@
 s \not{\xrightarrow{a}}    \}\] and replace deadlock reducing, under (3) by
-\[\forall t \in \mathcal{T}_{A_1} \cap  \mathcal{T}_{A_2},\, \bot_{A_2}(t) \subseteq  \bot_{A_1}(t)  \] }
-
-\TODO{thm: backward compatibility + simulation is equivalent to extension refinement in case there is no hole and no guard, i.e. in case the definitions of automata coincide}
+%\[\forall t \in \mathcal{T}_{A_1} \cap  \mathcal{T}_{A_2},\, \bot_{A_2}(t) \subseteq  \bot_{A_1}(t)  \] } 
+%
+%\TODO{thm: backward compatibility + simulation is equivalent to extension refinement in case there is no hole and no guard, i.e. in case the definitions of automata coincide}
 
@@
 \end{lemma}
+
+Now that we have a refinement relation that takes both variable parameters and process parameters into account, we would like to ensure that it has  properties one would expect for a refinement relation.
 

### 2022-07-13 2021-Refinement/paper/refinementarticle.tex
strong bisim

@@
  \end{definition}
-
+Technically, the following sections do not rely on the definition of strong bisimulation on OA, but they follow the same principles and in particular the same way to faithfully simulate an open transition by a set of other open transitions.
 \begin{comment}
@@
 
+\begin{example} 
 To illustrate the refinement simulation of open automata, consider a variation on the \texttt{database} automaton of Fig.

### 2022-07-14 2021-Refinement/paper/refinementarticle.tex
Removed solved TODOs and added an explanation to prevent a likely (IMO) confusion

--- 2022-07-13 2021-Refinement/paper/refinementarticle.tex
@@
 \author{
-Rabéa Ameur-Boulifa\inst{1}\orcidID{0000-0002-2471-8012} \and
-Quentin Corradi\inst{2}\orcidID{} \and
-Ludovic Henrio \inst{2}\orcidID{0000-0001-7137-3523} \and
-Eric Madelaine \inst{3}\orcidID{0000-0002-5552-5993}}
+Rabéa\inst{1}\orcidID{1111-2222-3333-4444} \and
+Quentin\inst{1,2}\orcidID{1111-2222-3333-4444} \and
+Ludo\inst{2}\orcidID{0000-1111-2222-3333} \and
+Eric\inst{3}\orcidID{2222--3333-4444-5555}}
 %
@@
 %
-\institute{LTCI, T\'el\'ecom Paris, Institut Polytechnique de Paris, France
-\email{first.last@telecom-paris.fr}\\
-\and
-Universit\'e Lyon, EnsL, UCBL, CNRS, Inria,  LIP France\\
-\email{first.last@ens-lyon.fr}
- \and
-INRIA Sophia Antipolis M\'edit\'erann\'ee, UCA,  Sophia Antipolis, France
-\email{first.last@inria.fr}}
+\institute{blabla
+\email{lncs@fff}\\
+\url{http://www.springer.com/gp/computer-science/lncs} \and
+blibli\\
+\email{\{abc,def\}@fff}}
 %
@@
 
-\TODO{Entete : rabea}
-
-\TODO{explication bisim: Ludo}
-
 Automata are convenient for specifying and verifying systems, but most automata definitions allow only the specifications of finite closed systems.
@@
 This definition, which is based on systems whose behaviour is fully defined, is not well-suited for open systems,  as it requires to reason also about unspecified behaviours.
+% TODO: This version of simulation/trace inclusion doesn't fit our needs for another reason,
+% in our case all behaviours of the implementation do actually belong to the behaviours of the specification with our refinement (it seems counter-intuitive so it may be worth explaining):
+% Our specifications says "you must do that the way you choose to do it" (more precisely "the way the automaton in this hole chooses to do it as long as the guard is satisfied"), the implementation says "I do that this specific way"
+% so the behaviour of the implementation is a behaviour allowed by the specification, in particular it is included in the behaviours (of/allowed by) the specification
 
@@
 This section presents our notations and the principles of automata.
-Except for minor changes in the notations, compared to previous works~\cite{fhbisim} the only new contribution is the definition of a composition operator for open automata.
+Except for minor changes in the notations, compared to previous works~\cite{pnets} the only new contribution is the definition of a composition operator for open automata.
 %
@@
 \end{definition}
-
-We use two operators to access pieces of information of the OA.
 
@@
 
-\paragraph{Open automaton composition.}
+\paragraph{Open automaton composition}
 
@@
 \begin{definition}[Composition of open automata] \label{Def:CompOA}
-% TODO: this definition is a bit strange, why is Ac in the hole of Ap but the hole is in Ac and the notation is reversed?
 The composition of \(A_p = \OAg[p]\) in the hole \(k \in J_c\) of    \(A_c = \OAg[c]\) is the OA defined as follows:
 \[A_c\subst{A_p}{k} ::=  \OA{S_c \times S_p}{\mpar{s_{0c}, s_{0p}}}{V_c \uplus V_p}{\sigma_{0c} \uplus \sigma_{0p}}{J_p \uplus J_c \setminus \mbrc{k}}{T} \] \text{with }
-\begin{align*}
-T\!=& \mset{\OT{\mpar{s_c, s_p}}{\mpar{s'_c, s'_p}}{\alpha_c}{\beta_j^{j \in J'_p \uplus J'_c}\!}{g_c \wedge g_p \wedge \alpha_p = \beta_k}{\psi_c \uplus \psi_p}}{ \OT{s_c}{s'_c}{\alpha_c}{\beta_j^{j \in J'_c \uplus \mbrc{k} }\!}{g_c}{\psi_c} \in\!
-T_c, \OTx{p}{}{}{p} \in\!
-T_p} \\
+
+\begin{align*}
+T=& \mset{\OT{\mpar{s_c, s_p}}{\mpar{s'_c, s'_p}}{\alpha_c}{\beta_j^{j \in J'_p \uplus J'_c}}{g_c \wedge g_p \wedge \alpha_p = \beta_k}{\psi_c \uplus \psi_p}}{ \OT{s_c}{s'_c}{\alpha_c}{\beta_j^{j \in J'_c \uplus \mbrc{k} }}{g_c}{\psi_c} \in T_c, \OTx{p}{}{}{p} \in T_p} \\
 	& \cup \mset{\OT{\mpar{s_c, s_p}}{\mpar{s'_c, s_p}}{\alpha_c}{\beta_j^{j \in J'_c}}{g_c}{\psi_c}}{\OTx{c}{}{}{c} \in T_c, k \notin J'_c, s_p \in S_p}
@@
    \includegraphics[width=.3\textwidth]{Figures/compose_count_db.pdf}
-   \caption{(Left) Open Automaton of \texttt{counter} process.
+   \caption{(left) Open Automaton of \texttt{counter} process.
 Its role is to get a target, then count ticks until that target is reached, then emits an action with the elapsed time and restart.
-(Right) Open Automaton of the composition \texttt{database}[\texttt{counter/cnt}].\label{Fig:counter}}
+(right) Open Automaton of the composition \texttt{database}[\texttt{counter/cnt}].\label{Fig:counter}}
 \end{figure}
@@
 
-\paragraph{Relations between open automata.}
+\paragraph{Relations between open automata}
 A relation (bisimulation, refinement, etc.) between OA requires to compare their states.
 To do so we will suppose that the variables of the two OA are disjoint (a renaming of variables may have to be applied before comparing OA states).
-\begin{definition}[Relation on OA configurations] Suppose $V_1$ and $V_2$ are disjoint.
-A relation on configurations of \(\OAg[1]\) and \(\OAg[2]\) is a function \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
+\begin{definition}[Relation on OA states] Suppose $V_1$ and $V_2$ are disjoint.
+A relation on states of \(\OAg[1]\) and \(\OAg[2]\) is a function \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
 \end{definition}
-%\TODO{C'est etrange, la formulation "the variables they refer to", comme il n'y a plus de variables d'etat... +1}
-The idea is that two states are related depending on the state of the automaton, i.e. if the variables of the OA verify a certain formula. 
-In other words, for each pair of states, a boolean formula that may refer to the  variables of each of the two OA states whether the two states are related or not.
+\TODO{C'est etrange, la formulation "the variables they refer to", comme il n'y a plus de variables d'etat... +1}
+The idea is that two states are related if the variables they refer to verify a certain formula.
 Additionally, we may check that initial states of the automata are related by checking that: \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\).
@@
 
-\paragraph{A bisimulation for open automata.}
-
-Bisimulation between OA was defined in~\cite{fhbisim}. Instead of recalling its definition we show below the principles of this bisimulation.
+\paragraph{A bisimulation for open automata}
+
+Bisimulation between OA was defined in~\cite{fh-bisim}. Instead of recalling its definition we show below the principles of this bisimulation.
 \TODO{Je ne comprends pas cette figure... elle est incomplete ? Ou alors il faut un peu d'explications...}
@@
 
-Similarly to FH-bisimulation~\cite{fhbisim} we are interested  in finding relations between configurations of two open automata that contain variables and holes.
+Similarly to FH-bisimulation~\cite{fhbisim} we are interested  in finding relations between states of two open automata that contain variables and holes.
 However here we want to build a refinement relation that  also guarantees that no deadlock is introduced when refining the automaton (at least not among the scenarios originally planned in the specification).
@@
 More precisely, a refinement relation characterizes when two states are related, and this  characterisation is expressed as a predicate on the variables of the two automata.
-Thus, a refinement relation is a relation on OA configurations.
+Thus, a refinement relation is a relation on OA states.
 
@@
 %The idea is that 
-We rely on a classical notion of simulation inspired from~\cite{fhbisim}.
-The idea is that two configurations related by a relation; if one state can do a transition, then the other can do a transition too.
+We rely on a classical notion of simulation inspired from~\cite{fh-bisim}.
+The idea is that two states related by a given relation and states that if one state can do a transition, then the other can do a transition too.
 But to limit the creation of deadlocks when simulating an automaton, we first define when a relation is preserved along identical transitions before characterising a first simple refinement relation  to compare automata with identical holes.
@@
 
-Let us first explain the reasons why simulation can introduce allow undesired behaviours to emerge and how we want to limit them. 
+Let us first explain the reasons why simulation can introduce allow undesired bwhaviours to emerge and how we want to limit them. 
 The automaton that simulates a specification features any behaviour that contains the behaviour of the specification, or more precisely, for each state that simulates a state of the specification, the simulating automaton must at least feature the behaviour of the specification.
@@
 \bigsymb{\bigexists} 
-\mpar{t_{1x} \!=\! \OTx{1}{x}{1x}{1x} \!\in\! \fOT{s_1}}^{x \in X}\!,
- V_1 \uplus V_2 \uplus \biguplus_{x\in X}\!\fvars{t_{1x}} \uplus \fvars{t_2} \uplus \fvars{t_1} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 
+\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},
+ V_1 \uplus V_2 \uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_2} \uplus \fvars{t_1} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 
 %\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} 
@@
 
-\TODO{[LUDO]
-We define here simulation between labelled transition systems to Hole-equal simulation  between  open automata that have exactly the same holes. }
+\medskip
+
+We define here simulation between labelled transition systems to Hole-equal simulation  between  open automata that have exactly the same holes.
 \begin{definition}[Hole-equal simulation]
@@
 %Note also the second part of the conjunction of condition (2) expresses the deadlock reduction between automata (as introduced in Definition \ref{def:dpwd}).
-The first and second conditions coincide with the natural way to prove inductively that an automaton simulates another by starting with the initial state.
-The third condition ensures that the refinement relation prevents the introduction of deadlocks.
+\TODO{The first and second conditions coincide with the natural way to prove inductively that an automaton simulates another by starting with the initial state.
+The third condition ensures that the refinement relation prevents the introduction of deadlocks.}
 
@@
 With such a relation we are able to check the refinement between two open automata with the same level of abstraction but specified differently, for example, by duplicating states, removing transitions,  reinforcing  guards, modifying variables.
-\begin{example} 
+
 To illustrate the refinement simulation of open automata, consider a variation on the \texttt{database} automaton of Fig.
@@
 We suppose that on more concrete level, in addition to querying and updating the data base,  a backup copy of it may also be made.
-\end{example}
-\begin{figure}[!tb]
+
+\begin{figure}[h]
  \centering
@@
 
-The refinement relation  also specifies that the refined process must follow the behaviour of the specification, not only at every compatible state but also along any scenario of the specification.
-We will show in Section~\ref{sec:prop} that this refinement relation has good properties in terms of transitivity, compositionality, and reflexivity.
+\TODO{The refinement relation  also specifies that the refined process must follow the behaviour of the specification, not only at every compatible state but also along any trace.}
+
+ We will show in Section~\ref{sec:prop} that this refinement relation has good properties in terms of transitivity, compositionality, reflexivity, etc.
 
@@
 %Technically,  it expresses how the concepts from the abstract and the refined systems are linked together.
+
+\TODO{add an example}
 
@@
 \begin{definition}[Open automata refinement]\label{Def:OA-Refinement}
-For two open automata\\ \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a refinement of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a relation on configurations $R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that:
+For two open automata\\ \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a refinement of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a relation $R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that:
 \item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
@@
 
-\TODO{[LUDO] relire et virer le rouge}
 This definition leads to a notion of simulation as refinement the same as the one used in LOTOS \cite{Brinksma:87} and presented under the name extension refinement.
@@
 \end{lemma}
+\TODO{example}
 
 \section{Properties of our Refinement Relations}\label{sec:prop}
-
+\TODO{1.5 pages}
 We now  state the properties of our refinement relations, proofs of the properties can be found in the appendices.
@@
 
-% TODO: I don't understand this definition, why v = v on vars(s1), what about s2
-% ANS: was copy paste from the report, polished now
 The relation  \(\wrel{}{}{H}\) is reflexive,  \(\wrel{A}{A}{H}\).
@@
 More precisely, we define a relation of the following form:
+% TODO: this relation defines is
   \[R_{13}(s_1,s_3)=\bigvee_{s_2\in S_2}\mpar{R_{12}(s_1,s_2) \land R_{23}(s_2,s_3) } \]
-We then prove that this relation  is a refinement, according to Definition~\ref{Def:OA-Refinement}.
-
-The next  theorem states that if two automata are in refinement relation and the same automata is placed in the same hole of the two automata, then the refinement is preserved.
+We then prove that this relation defines is a refinement, according to Definition~\ref{Def:OA-Refinement}.
+
+The next  theorem states that if two automata are in refinement relation and the same automata is placed in the same hole of the two autaomata, then the refinement is rpreserved.
 This is the first step toward proving that
@@
 \begin{center}
-\includegraphics[scale=0.7]{Figures/Thm2intuition}
+\includegraphics[scale=0.7]{Figures/Theorem2bis}
 \end{center}
@@
 
-%\TODO{i did not put the global composition theorem, de we state it?}
-
-\TODO{[LUDO] proof sketch}
-
-\TODO{The subtlety here is that the original relation implies that valuations in A3 are equal (ie the value for each variable are the same in both valuations, modulo renaming), after a transition we should obtain ``equal'' valuations because Post are deterministic}
-
-\TODO{[RABEA] example : composition and refinement}
+\TODO{i did not put the global composition theorem, de we state it?}
 
 % TODO: why is there several ovoid stacked only on one side?
-%\begin{center}
-%\includegraphics[scale=0.7]{Figures/Theorem1}
-%\end{center}
+\begin{center}
+\includegraphics[scale=0.7]{Figures/Theorem1}
+\end{center}
 
@@
 
-\TODO{[RABEA] RW}
+\TODO{1 page}
 
@@
 
-\newpage
-
 \appendix
@@
 
-\TODO{[RABEA] proof}
 Let's consider any $s_{2p} \in (s_{2p})^{p\in P}$. According to the refinement relation between  $A_1$ and $A_2$ we have the following:
@@
 
+\TODO{The subtlety here is that the original relation implies that valuations in A3 are equal (ie the value for each variable are the same in both valuations, modulo renaming), after a transition we should obtain ``equal'' valuations because Post are deterministic}
+
 \proof
@@
 \end{align*}
-\item Second, we need to prove for any open transition $t_{13}$ in $T_{13}$ originating from $s_{13}$:
+\item Second, we need to prove for any OT $t_{13}$ in $T_{13}$ originating from $s_{13}$:
 \begin{align*}
@@
 
-We reason on the way the open transition $t_{23}$ has been obtained: either the hole $k$ of $A_2$ is involved in the transition or not.
+We reason on the way the OT $t_{23}$ has been obtained: either the hole $k$ of $A_2$ is involved in the transition or not.
 
@@
 
-\item Second, we need to prove for any open transition $t_{12}$ in $T_{12}$ originating from $s_{12}$
+\item Second, we need to prove for any OT $t_{12}$ in $T_{12}$ originating from $s_{12}$
 
@@
 
-We reason on the way the open transition $t_{13}$ has been obtained: either the hole $k$ of $A_1$ is involved in the transition or not.
+We reason on the way the OT $t_{13}$ has been obtained: either the hole $k$ of $A_1$ is involved in the transition or not.
 

### 2022-07-14 2021-Refinement/paper/refinementarticle.tex
proof sketch

--- 2022-07-13 2021-Refinement/paper/refinementarticle.tex
@@
 
-\TODO{[LUDO] proof sketch}
-
-\TODO{The subtlety here is that the original relation implies that valuations in A3 are equal (ie the value for each variable are the same in both valuations, modulo renaming), after a transition we should obtain ``equal'' valuations because Post are deterministic}
+The bisimulation relation that we consider is the one that makes $A_1$ and $A_2$ bisimilar, complemented with identity of configurations for $A_3$.
+The proof relies on the fact that, by construction, all transitions of the composed automaton $A_1\subst{A_3}{k}$ are specified by open transitions of $A_1$.
+For the transitions that do not involve hole $k$, the transition of $A_1\subst{A_3}{k}$ is the same and simulation between $A_1$ and $A_2$ allows us to conclude directly.
+If the hole $k$ is involved the considered relation  implies that valuations in A3 are equal (ie the value for each variable are the same in both valuations), after a transition we should obtain ``equal'' valuations because Post are deterministic.
 

### 2022-07-15 2021-Refinement/paper/refinementarticle.tex
examples

@@
 Rabéa Ameur-Boulifa\inst{1}\orcidID{0000-0002-2471-8012} \and
-Quentin Corradi\inst{2}\orcidID{} \and
+Quentin Corradi\inst{2}\orcidID{0000-0003-4218-3987} \and
 Ludovic Henrio \inst{2}\orcidID{0000-0001-7137-3523} \and
@@
 \and
-Universit\'e Lyon, EnsL, UCBL, CNRS, Inria,  LIP France\\
+Universit\'e Lyon, EnsL, UCBL, CNRS, Inria,  LIP, France\\
 \email{first.last@ens-lyon.fr}
  \and
-INRIA Sophia Antipolis M\'edit\'erann\'ee, UCA,  Sophia Antipolis, France
+INRIA Sophia Antipolis M\'edit\'erann\'ee, UCA,  France
 \email{first.last@inria.fr}}
@@
 \section{Introduction}
-
-\TODO{Entete : rabea}
 
@@
  \centering
-   \includegraphics[width=.5\textwidth]{Figures/counter.pdf}\hfill 
-   \includegraphics[width=.3\textwidth]{Figures/compose_count_db.pdf}
+   \includegraphics[width=.55\textwidth]{Figures/counter.pdf}\hfill 
+   \includegraphics[width=.35\textwidth]{Figures/compose_count_db.pdf}
    \caption{(Left) Open Automaton of \texttt{counter} process.
@@
 \end{figure}
+
+\begin{example}
 In Fig.
@@
 The composed automaton  takes over  the same steps as the   \texttt{database} automaton but it also includes new steps,  indicating the change of states for the setting of timer.
+Note how restricting the composition to a synchronisation of actions (of the encompassing automaton and  of the hole) corresponds to imposing of a change in states.
+This example also shows how value passing works: the time limit of the counter is set by the parameter \texttt{n} carried by  the \texttt{set} action.
+\end{example}
 
@@
 \begin{definition}[Relation on OA configurations] Suppose $V_1$ and $V_2$ are disjoint.
-A relation on configurations of \(\OAg[1]\) and \(\OAg[2]\) is a function \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
+A relation on configurations of two OA \(\OAg[1]\) and \(\OAg[2]\) is a function \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
 \end{definition}
@@
 The presence of holes in fact raises no strong difficulty here.
-Consider the two following simple OA.
+Consider the two following simple OA:
 
@@
 We should check that these two transitions cover all the cases accepted by te right hand side OA, and of course that destination states are in relation.
-Formally, fh-bisimulation is defined \cite{fhbisim} as follows
+Formally, fh-bisimulation is defined \cite{fhbisim} as follows:
 
@@
 We define now a simulation between OA that have the same set of holes.
-This relation thus focuses on the simulation of transitions and uses the previous definition to prevent the refined automaton from nondeterministically reaching states that introduce deadlocks in a scenario planned without deadlock in the specification.
+This relation thus focuses on the simulation of transitions and uses the previous definition to prevent the refined automaton from non-deterministically reaching states that introduce deadlocks in a scenario planned without deadlock in the specification.
 \begin{definition}[Hole-equal simulation]
@@
 \begin{example} 
-To illustrate the refinement simulation of open automata, consider a variation on the \texttt{database} automaton of Fig.
-\ref{Fig:RefineOA}.
+To illustrate the refinement simulation of open automata, consider a variation on the \texttt{database}.
 We suppose that on more concrete level, in addition to querying and updating the data base,  a backup copy of it may also be made.
+The behaviour of the concrete database is given by
+an open automaton  depicted in Fig. \ref{Fig:RefineOA}. 
 \end{example}
@@
    \includegraphics[width=.9\textwidth]{Figures/databaseRefine.pdf}
-   \caption{The refined Open Automaton of the automaton of Fig.\ref{Fig:SpecOA}.
-Two other actions,  in addition to  \texttt{qry} and \texttt{upd},  \texttt{back} representing a request to make a backup copy and    \texttt{cpy} is used to reflect the actual operation of copying.
+   \caption{Another variant of the \texttt{database} process.
+Two other actions,  in addition to  \texttt{qry} and \texttt{upd},  \texttt{back} representing a request to make a backup copy and    \texttt{cpy} are used to reflect the actual operation of copying.
 \label{Fig:RefineOA}}
@@
 %Technically,  it expresses how the concepts from the abstract and the refined systems are linked together.
-
-\begin{figure}[h]
- \centering
-   \includegraphics[width=.6\textwidth]{Figures/composeRefined.pdf}
-   \caption{The refined Open Automaton composed with the counter \label{Fig:ComposeRefine}}
-\end{figure}
 
@@
 Note that every action of the holes outside \(H\) is unconstrained in the related automata.
+
+\begin{example} It is easy to see the  open automaton of Fig.~\ref{Fig:RefineOA} is a refinement the open automaton of Fig.~\ref{Fig:SpecOA} according to this definition.
+\end{example}
 
@@
 
-The next  theorem states that if two automata are in refinement relation and the same automata is placed in the same hole of the two automata, then the refinement is preserved.
+The next  theorem states that if two automata are in refinement relation and the same automaton is placed in the same hole of the two automata, then the refinement is preserved.
 This is the first step toward proving that
  refinement is compositional in the sense that it is sufficient to prove refinement for the composed automata separately to obtain a refinement relation.
-The second part, i.e. proving that placing in the same context two OA in refinement, we obtain two OA in refinement is left for future works.
+The second part, i.e. proving that placing in the same context two open automata in refinement, we obtain two open automata in refinement is left for future works.
 %
@@
 For the transitions that do not involve hole $k$, the transition of $A_1\subst{A_3}{k}$ is the same and simulation between $A_1$ and $A_2$ allows us to conclude directly.
-If the hole $k$ is involved the considered relation  implies that valuations in A3 are equal (ie the value for each variable are the same in both valuations), after a transition we should obtain ``equal'' valuations because Post are deterministic.
-
-\TODO{[RABEA] example : composition and refinement}
+If the hole $k$ is involved the considered relation  implies that valuations in $A_3$ are equal (i.e the value for each variable are the same in both valuations), after a transition we should obtain ``equal'' valuations because post-conditions are deterministic.
+\begin{example} The composition of the refined \texttt{database} and the \texttt{counter} is again an open automata depicted in Fig.~\ref{Fig:ComposeRefine}.
+\end{example}
+
+\begin{figure}[h]
+ \centering
+   \includegraphics[width=.6\textwidth]{Figures/composeRefined.pdf}
+   \caption{Open automata resulting from the composition of the  refined  \texttt{database} and the \texttt{counter} \label{Fig:ComposeRefine}}
+\end{figure}
 
@@
 
+\newpage
 \TODO{[RABEA] proof}
-Let's consider any $s_{2p} \in (s_{2p})^{p\in P}$. According to the refinement relation between  $A_1$ and $A_2$ we have the following:
-
-\begin{multline*}
-\bigforall \mpar{s_1, s_{2p}} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_{2p}} = \mpar{\OTx{1}{}{1}{1}, \OTx{2p}{}{2p}{2p}} \in \fOT{s_1} \times \fOT{s_{2p}} \\ 
+Let's consider any $s_{2p} \in (s_{2p})^{p\in P}$. According to the refinement relation between  $A_1$ and $A_2$ we have for any open transition $t_1$ in $T_1$  originating from $s_1$:
+\begin{align*}
+\OTx{1}{}{1}{1} \in \fOT{s_1}
+\end{align*}
+there exists an indexed family of OTs originating from $s_{2p}$: 
+\begin{align*}
+\mpar{\OTx{2p}{x}{2px}{2px} \in \fOT{s_{2p}}}^{x \in X_p} 
+\end{align*}
+such that $\forall x \in X, J'_{2px} \cap H = J'_1 \cap H$ and
+\begin{multline*}
+%\everymath{\displaystyle}
+V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\ \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X_p} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \nwedge\\
+			 g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}}
+		\end{array}}} 
+\end{multline*}	
+According to the refinement  relation between   $A_2$ and $A_3$, we know the following is satisfied, in particular for  the set $(t_{2pxy})^{x\in X_p}$:
+\begin{multline*}
+\bigforall \mpar{s_{2p}, s_3} \in S_1 \times S_3, \bigsymb{\forall} \mpar{t_{2px}, t_3} = \mpar{\OTx{2px}{}{2px}{2px}, \OTx{3}{}{3}{3}} \in \fOT{s_{2p}} \times \fOT{s_3} \\ 
 \bigsymb{\bigexists} 
-\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},
- V_1 \uplus V_2 \uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_{2p}} \vdash \hspace{6cm}\\  R_{12}\mpar{s_1, s_{2p}} \wedge 	g_1 \wedge g_{2p} \wedge \alpha_1 = \alpha_{2p}
-%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2p}} \beta_{1j} = \beta_{2pj} 
+\mpar{t_{2pxy} = \OTx{2px}{y}{2pxy}{2pxy} \in \fOT{s_{2p}}}^{y \in Y},
+V_2 \uplus V_3\uplus \biguplus_{y\in Y}\fvars{t_{2pxy}} \uplus \fvars{t_3} \uplus \fvars{t_{2p}} \vdash \hspace{6cm}\\  R_{23}\mpar{s_{2p}, s_3} \wedge 	g_{2px}\wedge g_3 \wedge \alpha_{2px}= \alpha_3
+%\wedge \bigwedge_\subbox{j \in J'_2 \cap J'_3} \beta_{2pj} = \beta_{3j} 
+\implies \hspace{6cm}\\
+%\exists
+%\OTx{1}{a}{3}{3}\in \fOT{s_2}. \\
+\bigsymb{\bigwedge_{y\in Y}}
+\mpar{
+\alpha_{2px}=\alpha_{2p xy}  \land J'_{2pxy}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{2pxyj}\land g_{2p xy}\land
+ R_{23}\mpar{s'_{2p xy}, s'_3}\psubst{\psi_{2p xy} \uplus \psi_3}}\\
+\end{multline*}
+Yet according to the refinement  relation between  $A_1$ and $A_2$ the following is satisfied, in particular over the family of transitions in $Y$:
+\begin{multline*}
+\bigforall \mpar{s_1, s_{2p}} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_{2pxy}} = \mpar{\OTx{1}{}{1}{1}, \OTx{2pxy}{}{2pxy}{2pxy}} \in \fOT{s_1} \times \fOT{s_{2p}} \\ 
+\bigsymb{\bigexists} 
+\mpar{t_{1z} = \OTx{1}{z}{1z}{1z} \in \fOT{s_1}}^{z \in Z},
+ V_1 \uplus V_2 \uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_{2p}} \vdash \hspace{6cm}\\  R_{12}\mpar{s_1, s_{2p}} \wedge 	g_1 \wedge g_{2pxy} \wedge \alpha_1 = \alpha_{2pxy}
+%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2p}} \beta_{1j} = \beta_{2pxyj} 
 \implies \hspace{6cm}\\
@@
 %\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
-\bigsymb{\bigwedge_{x\in X}}
+\bigsymb{\bigwedge_{z\in Z}}
 \mpar{
-\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_{2p} \land \bigwedge_\subbox{j \in J'_{2p} } \beta_{2pj} = \beta_{1xj}\land g_{1 x}\land
- R_{12}\mpar{s'_{1 x}, s'_{2p}}\psubst{\psi_{1 x} \uplus \psi_{2p}}}
-\end{multline*}
+\alpha_1=\alpha_{1 z}  \land J'_{1z}= J'_{2pxy} \land \bigwedge_\subbox{j \in J'_{2pxy} } \beta_{2pxyj} = \beta_{1zj}\land g_{1 z}\land
+ R_{12}\mpar{s'_{1 z}, s'_{2pxy}}\psubst{\psi_{1 z} \uplus \psi_{2pxy}}}
+\end{multline*}
+
+From previous formulas we get:
+
+\begin{multline*}
+\mpar{R_{12}\mpar{s_1, s_{2p}} \wedge 	g_1 \wedge g_{2pxy} \wedge \alpha_1 = \alpha_{2pxy}} \wedge \mpar{ R_{23}\mpar{s_{2p}, s_3} \wedge 	g_{2px}\wedge g_3 \wedge \alpha_{2px}= \alpha_3 } 
+\implies \hspace{6cm}\\
+%\exists
+%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
+\bigsymb{\bigwedge_{z\in Z}}
+\mpar{
+\alpha_1=\alpha_{1 z}  \land J'_{1z}= J'_{2pxy} \land \bigwedge_\subbox{j \in J'_{2pxy} } \beta_{2pxyj} = \beta_{1zj}\land g_{1 z}\land
+ R_{12}\mpar{s'_{1 z}, s'_{2pxy}}\psubst{\psi_{1 z} \uplus \psi_{2pxy}}} \wedge \\\bigsymb{\bigwedge_{y\in Y}}
+\mpar{
+\alpha_{2px}=\alpha_{2p xy}  \land J'_{2pxy}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{2pxyj}\land g_{2p xy}\land
+ R_{23}\mpar{s'_{2p xy}, s'_3}\psubst{\psi_{2p xy} \uplus \psi_3}}
+\end{multline*}
+
+--------------------------------------------------
 

### 2022-07-15 2021-Refinement/paper/refinementarticle.tex
cont.

@@
 For the transitions that do not involve hole $k$, the transition of $A_1\subst{A_3}{k}$ is the same and simulation between $A_1$ and $A_2$ allows us to conclude directly.
-If the hole $k$ is involved the considered relation  implies that valuations in $A_3$ are equal (i.e the value for each variable are the same in both valuations), after a transition we should obtain ``equal'' valuations because post-conditions are deterministic.
+If the hole $k$ is involved the considered relation  implies that valuations in $A_3$ are equal (i.e., the value for each variable are the same in both valuations), after a transition we should obtain ``equal'' valuations because post-conditions are deterministic.
 \begin{example} The composition of the refined \texttt{database} and the \texttt{counter} is again an open automata depicted in Fig.~\ref{Fig:ComposeRefine}.
+As stated by the theorem, this automaton is a refinement of the automaton of the figure Fig.~\ref{Def:CompOA}, the automaton resulting from the composition of the abstract \texttt{database}.
 \end{example}

### 2022-07-17 2021-Refinement/paper/refinementarticle.tex
related work

@@
 
+Pictorially, the theorem has the following form:
+
 \begin{center}
@@
 If the hole $k$ is involved the considered relation  implies that valuations in $A_3$ are equal (i.e., the value for each variable are the same in both valuations), after a transition we should obtain ``equal'' valuations because post-conditions are deterministic.
-\begin{example} The composition of the refined \texttt{database} and the \texttt{counter} is again an open automata depicted in Fig.~\ref{Fig:ComposeRefine}.
-As stated by the theorem, this automaton is a refinement of the automaton of the figure Fig.~\ref{Def:CompOA}, the automaton resulting from the composition of the abstract \texttt{database}.
+\begin{example} The composition of the refined \texttt{database} and the \texttt{counter} is again an open automata, depicted in Fig.~\ref{Fig:ComposeRefine}.
+As stated by the theorem,  it can easily be verified that this automaton is a refinement of the automaton of the figure Fig.~\ref{Def:CompOA}, i.e.
+the automaton resulting from the composition of the abstract \texttt{database}.
 \end{example}
@@
 \label{sec:sota}
-
-\TODO{[RABEA] RW}
 
@@
 
-Previous work on open automata focused on equivalence relations compatible with composition.
-In an article by Hou, Zechen and Madelaine \cite{10.1145/3372884.3373161}, a computable bisimulation is introduced and proved equivalent to the previous bisimulation already introduced.
-In a more recent work by Ameur-Boulifa, Henrio and Madelaine \cite{fhbisim}, a weak version of the bisimulation on open automata is introduced.
-These works differ from ours because the relation introduced in this report is a refinement relation in the form of a simulation and not a bisimulation.
-Also we do not have results as strong as computability neither a weak version able to tackle silent actions.
-
-\TODO{Some related work on other models than open automata introduce refinement relations.
-In a chapter by Bellegarde, Julliand and Kouchnarenko \cite{10.1007/3-540-46428-X_19}, a simulation relation on transition systems is introduced.
-This simulation encompass action refinement, is able to deal with silent actions and is compatible with parallel composition.
-Here the refinement relation does not consider action refinement as valid but it should be done in future work.
-Also they check how LTL properties are preserved or combined using their refinement which we do not do.
-However their model is less expressive: the transition system model is less expressive than open automata and the parallel composition is less expressive than composition on open automata.
-In a later report by Kouchnarenko and Lanoix \cite{10.1007/978-3-540-70881-0_26}, the refinement relation they introduce is on LTS (labelled transition systems).
-Their relation additionally prevents deadlock and livelocks.
-The composition is also extended to synchronised composition which is more expressive.
-In our work we also deal with deadlocks but not with livelocks since the latter arise only with silent actions.
-This work is closer than the previous one to what we do here, still open automata are more expressive than LTS and composition is more general than synchronised composition.}
-
-A refinement relation on models nearer to open automata is introduced in an article by Zhang, Meng and Lo \cite{Zhang2014}.
-In their article they work with transition systems with variable which makes the state space potentially infinite.
-This aspect is also present in open automata.
-They show how invariants are composed.
-By relation on these invariants they introduce several refinement relations.
-We could have done something similar for non-blocking composition reachability predicates which are introduced in Section \ref{sec:proofelts}.
-
-On the deadlock prevention aspect, an article by Dihego, Sampaio and Oliveira \cite{DIHEGO2020110598} present a refinement relation on process algebra (translated to LTS).
-This refinement relation is a special case of inheritance and prevents the introduction of deadlocks.
-Their refinement and inheritance are quite the opposite of our refinement in terms of new behaviours.
-They have channels, interfaces, inputs and outputs, which in the open automata model can be compared to action labels, holes and action data for both inputs and outputs.
-They have a rich composition as open automata but the introduction of deadlock is already prevented by a well chosen set of composing operations.
-Also their composition is slightly different than the one on open automata because they can cause loops by linking two channels of the same process, where in open automata the composition makes an oriented tree.
-In their model there is an explicit deadlock and a successful termination where in open automata there are no explicit termination.
-We define a deadlock as a configuration without possible transition and assume what is a deadlock when comparing the open automata.
-To define their refinement and inheritance relation they use trace and failure semantics, which are weaker than (bi)simulations \cite{10.5555/640428.640430} and could break with open automata composition.
+Previous works on open automata focused on equivalence relations compatible with composition.
+In  \cite{10.1145/3372884.3373161}, a computable bisimulation is introduced, while in \cite{fhbisim} is introduced a weak version of the bisimulation on open automata. 
+In this paper we tackle the refinement relation in the form of simulation, as is the case for the corresponding relations on labelled transition systems \cite{10.1007/3-540-46428-X_19}.
+But unlike the standard simulation we deal with symbolic and open models.
+In \cite{Zhang2014}, the authors exploit transition systems to reason about the systems  that are partially specified by using variables, making  the state space potentially infinite.
+
+The simulation  ensures the preservation of   
+safety properties as deadlock-freeness  and, more generally, all 
+all linear temporal logic properties.
+The issue is about the properties of simulation, in particular closure properties such as preservation under composition.
+Some works   have addressed the problem of non-introduction of blocking by composition.
+For example, in \cite{DIHEGO2020110598} it is presented a refinement relation on process algebra based on failure semantics that is basically different from the (bi)simulation\cite{10.5555/640428.640430}.
 
@@
 \TODO{[RABEA] proof}
-Let's consider any $s_{2p} \in (s_{2p})^{p\in P}$. According to the refinement relation between  $A_1$ and $A_2$ we have for any open transition $t_1$ in $T_1$  originating from $s_1$:
+Let's consider any $s_{2p} \in (s_{2p})^{p\in P}$. According to the refinement relation between  $A_1$ and $A_2$, we have  the following formula that we denote ($*$):\\
+for any open transition $t_1$ in $T_1$  originating from $s_1$:
 \begin{align*}
@@
 \end{multline*}	
-According to the refinement  relation between   $A_2$ and $A_3$, we know the following is satisfied, in particular for  the set $(t_{2pxy})^{x\in X_p}$:
-\begin{multline*}
-\bigforall \mpar{s_{2p}, s_3} \in S_1 \times S_3, \bigsymb{\forall} \mpar{t_{2px}, t_3} = \mpar{\OTx{2px}{}{2px}{2px}, \OTx{3}{}{3}{3}} \in \fOT{s_{2p}} \times \fOT{s_3} \\ 
+On the other hand, according to the refinement relation between   $A_2$ and $A_3$, we know condition 3 is satisfied, $\bigforall \mpar{s_{2p}, s_3} \in S_1 \times S_3$ and $\bigsymb{\forall} \mpar{t_{2p}, t_3} \in \fOT{s_{2p}} \times \fOT{s_3}$ and in particular for  the set $(t_{2px})^{x\in X_p}$ so we  have the following that we denote ($**$):
+\begin{multline*}
+\bigsymb{\forall} \mpar{t_{2px}, t_3} = \mpar{\OTx{2px}{}{2px}{2px}, \OTx{3}{}{3}{3}} \in \fOT{s_{2p}} \times \fOT{s_3} \\ 
 \bigsymb{\bigexists} 
-\mpar{t_{2pxy} = \OTx{2px}{y}{2pxy}{2pxy} \in \fOT{s_{2p}}}^{y \in Y},
+\mpar{t_{2pxy} = \OTx{2px}{y}{2pxy}{2pxy} \in \fOT{s_{2p}}}^{y \in Y_X},
 V_2 \uplus V_3\uplus \biguplus_{y\in Y}\fvars{t_{2pxy}} \uplus \fvars{t_3} \uplus \fvars{t_{2p}} \vdash \hspace{6cm}\\  R_{23}\mpar{s_{2p}, s_3} \wedge 	g_{2px}\wedge g_3 \wedge \alpha_{2px}= \alpha_3
@@
 %\OTx{1}{a}{3}{3}\in \fOT{s_2}. \\
-\bigsymb{\bigwedge_{y\in Y}}
+\bigsymb{\bigwedge_{y\in Y_X}}
 \mpar{
@@
 \end{multline*}
-Yet according to the refinement  relation between  $A_1$ and $A_2$ the following is satisfied, in particular over the family of transitions in $Y$:
-\begin{multline*}
-\bigforall \mpar{s_1, s_{2p}} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_{2pxy}} = \mpar{\OTx{1}{}{1}{1}, \OTx{2pxy}{}{2pxy}{2pxy}} \in \fOT{s_1} \times \fOT{s_{2p}} \\ 
+Again according to the refinement  relation between  $A_1$ and $A_2$ and condition 3  the following is satisfied $\bigforall \mpar{s_1, s_{2p}} \in S_1 \times S_2$ , in particular over the family of transitions in $(t_{2pxy})^{y\in Y_X}$:
+\begin{multline*}
+\bigsymb{\forall} \mpar{t_1, t_{2pxy}} = \mpar{\OTx{1}{}{1}{1}, \OTx{2pxy}{}{2pxy}{2pxy}} \in \fOT{s_1} \times \fOT{s_{2p}} \\ 
 \bigsymb{\bigexists} 
@@
 
-From previous formulas we get:
-
-\begin{multline*}
+This is verified for all $y \in  Y_X$.
+\begin{multline*}
+\bigsymb{\bigwedge_{y \in  Y_X}}
+\Bigg[R_{12}\mpar{s_1, s_{2p}} \wedge 	g_1 \wedge g_{2pxy} \wedge \alpha_1 = \alpha_{2pxy}
+\implies \hspace{6cm}\\
+\bigsymb{\bigwedge_{z\in Z}}
+\mpar{
+\alpha_1=\alpha_{1 z}  \land J'_{1z}= J'_{2pxy} \land \bigwedge_\subbox{j \in J'_{2pxy} } \beta_{2pxyj} = \beta_{1zj}\land g_{1 z}\land
+ R_{12}\mpar{s'_{1 z}, s'_{2pxy}}\psubst{\psi_{1 z} \uplus \psi_{2pxy}}}\Bigg]
+\end{multline*}
+
+The conjunction of formulas ($*$) and ($**$) gives:
+\begin{multline*}
+\bigsymb{\bigwedge_{y \in  Y_X}}
+\Bigg[
 \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge 	g_1 \wedge g_{2pxy} \wedge \alpha_1 = \alpha_{2pxy}} \wedge \mpar{ R_{23}\mpar{s_{2p}, s_3} \wedge 	g_{2px}\wedge g_3 \wedge \alpha_{2px}= \alpha_3 } 
@@
 \alpha_1=\alpha_{1 z}  \land J'_{1z}= J'_{2pxy} \land \bigwedge_\subbox{j \in J'_{2pxy} } \beta_{2pxyj} = \beta_{1zj}\land g_{1 z}\land
- R_{12}\mpar{s'_{1 z}, s'_{2pxy}}\psubst{\psi_{1 z} \uplus \psi_{2pxy}}} \wedge \\\bigsymb{\bigwedge_{y\in Y}}
+ R_{12}\mpar{s'_{1 z}, s'_{2pxy}}\psubst{\psi_{1 z} \uplus \psi_{2pxy}}} \wedge \\
 \mpar{
@@
  R_{23}\mpar{s'_{2p xy}, s'_3}\psubst{\psi_{2p xy} \uplus \psi_3}}
-\end{multline*}
-
---------------------------------------------------
-
-Yet according to the refinement  relation between   $A_2$ and $A_3$ the following is satisfied:
-\begin{multline*}
-\bigforall \mpar{s_{2p}, s_3} \in S_1 \times S_3, \bigsymb{\forall} \mpar{t_{2p}, t_3} = \mpar{\OTx{2p}{}{2p}{2p}, \OTx{3}{}{3}{3}} \in \fOT{s_{2p}} \times \fOT{s_3} \\ 
-\bigsymb{\bigexists} 
-\mpar{t_{2px} = \OTx{2p}{x}{2px}{2px} \in \fOT{s_{2p}}}^{y \in Y},
-V_2 \uplus V_3\uplus \biguplus_{x\in X}\fvars{t_{2px}} \uplus \fvars{t_3} \uplus \fvars{t_{2p}} \vdash \hspace{6cm}\\  R_{23}\mpar{s_2, s_3} \wedge 	g_{2p}\wedge g_3 \wedge \alpha_2 = \alpha_3 
-%\wedge \bigwedge_\subbox{j \in J'_2 \cap J'_3} \beta_{2pj} = \beta_{3j} 
-\implies \hspace{6cm}\\
-%\exists
-%\OTx{1}{a}{3}{3}\in \fOT{s_2}. \\
-\bigsymb{\bigwedge_{x\in X}}
-\mpar{
-\alpha_{2p}=\alpha_{2p x}  \land J'_{2px}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{2xj}\land g_{2p x}\land
- R_{23}\mpar{s'_{2p x}, s'_3}\psubst{\psi_{2p x} \uplus \psi_3}}\\
-\end{multline*}
-For any open transition $t_{2px}$ originating from $s_{2p}$ we have 
-the following by definition of refinement between  $A_2$ and $A_3$:
-
-\begin{align*}
- \OTx{2p}{x}{2px}{2px} \in \fOT{s_{2p}} 
-\end{align*}
-there exists an indexed family of OTs originating from $s_3$: 
-\begin{align*}
-\mpar{\OTx{3}{pxy}{3pxy}{3pxy} \in \fOT{s_3}}^{y \in Y} 
-\end{align*}
-such that $\forall y \in Y, J'_{2px} \cap H = J'_{3py} \cap H$ and
-\begin{multline*}
-%\everymath{\displaystyle}
-V_2 \uplus V_3 \uplus \fvars{t_{2px}} \vdash\\
-R_{23}\mpar{s_{2p}, s_{3}} \wedge g_{2px} \implies  \operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			 \alpha_{2px}=\alpha_{3pxy} \wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H} \beta_{2pxj}=\beta_{3pxyj} \nwedge \\
-			g_{3pxy} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
-		\end{array}}  
-\end{multline*}
-
-Based on             the above two properties, we get:
-\begin{multline*}
-R_{12}\mpar{s_1, s_{2p}} \wedge  R_{23}\mpar{s_{2p}, s_{3}} \wedge	g_1 \wedge g_{2p} \wedge \alpha_1 = \alpha_{2p} 
-%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2p}} \beta_{1j} = \beta_{2pj} 
+ \Bigg]
+\end{multline*}
+By rearranging the formula we get:
+\begin{multline*}
+\bigsymb{\bigwedge_{y \in  Y_X}}
+\Bigg[
+R_{12}\mpar{s_1, s_{2p}} \wedge  R_{23}\mpar{s_{2p}, s_3} \wedge g_1 \wedge g_3 \wedge 	g_{2px}\wedge g_{2pxy} \wedge \alpha_1 = \alpha_{2pxy} \wedge     \alpha_{2px}= \alpha_3 
 \implies \hspace{6cm}\\
@@
 %\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
-\bigsymb{\bigwedge_{x\in X}}
-\operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			 \alpha_{2p}=\alpha_{3py} \wedge \bigwedge_\subbox{j \in J'_{3py} \cap H} \beta_{2pj}=\beta_{3pyj} \nwedge \\
-			g_{3py} \wedge R_{23}\mpar{s'_{2p}, s'_{3y}}\psubst{\psi_{2p} \uplus \psi_{3py}}
-		\end{array}}\bigwedge
-\mpar{\everymath{\displaystyle}\begin{array}{l}		
-\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_{2p} \land \bigwedge_\subbox{j \in J'_{2p}} \beta_{2pj} = \beta_{1xj} \land\\ g_{1 x} \land
- R_{12}\mpar{s'_{1 x}, s'_{2p}}\psubst{\psi_{1 x} \uplus \psi_{2p}}
- \end{array}}
+\bigsymb{\bigwedge_{z\in Z}}
+\mpar{
+\alpha_1=\alpha_{1 z}  \land J'_{1z}= J'_{2pxy} \land \bigwedge_\subbox{j \in J'_{2pxy} } \beta_{2pxyj} = \beta_{1zj}\land g_{1 z}\land
+ R_{12}\mpar{s'_{1 z}, s'_{2pxy}}\psubst{\psi_{1 z} \uplus \psi_{2pxy}}} \wedge \\
+\mpar{
+\alpha_{2px}=\alpha_{2p xy}  \land J'_{2pxy}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{2pxyj}\land g_{2p xy}\land
+ R_{23}\mpar{s'_{2p xy}, s'_3}  \psubst{\psi_{2p xy} \uplus \psi_3}}
+ \Bigg]
+\end{multline*}
+\TODO{ Je suis bloque a ce niveau: dans la conclusion on a $\alpha_{2px}=\alpha_{2p xy}$ qui est dans les hypotheses.  
 }
-\end{multline*}
-By  rearranging the terms in the formula we get:
-\begin{multline*}
-R_{12}\mpar{s_1, s_{2p}} \wedge  R_{23}\mpar{s_{2p}, s_{3}} \wedge	g_1 \wedge g_{2p} \wedge \operatorname*{\bigsymb{\bigvee}}_{y \in Y}\mpar{ \alpha_1 = \alpha_{2p} \wedge \alpha_{2p}=\alpha_{3py} \wedge g_{3py} }
-%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2p}} \beta_{1j} = \beta_{2pj} 
-\implies \hspace{6cm}\\
-%\exists
-%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
-\bigsymb{\bigwedge_{x\in X}}
-\operatorname*{\bigsymb{\bigvee}}_{y \in Y} 
-\mpar{\everymath{\displaystyle}\begin{array}{l}		
-\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_{2p} \land \bigwedge_\subbox{j \in J'_{2p}} \beta_{2pj} = \beta_{1xj} \land  \bigwedge_\subbox{j \in J'_{3py} \cap H} \beta_{2pj}=\beta_{3pyj} \\ g_{1 x}  \land
- R_{12}\mpar{s'_{1 x}, s'_{2p}} \wedge R_{23}\mpar{s'_{2p}, s'_{3y}} \psubst{\psi_{1 x} \uplus \psi_{2p}\uplus \psi_{3py}}
- \end{array}}
-\end{multline*}
 
 The formula is valid for all  $s_{2p} \in (s_{2p})^{p\in P}$. To build $R_{13}$ we need to rely on the disjunction of all possible path to relate $s_1$ and $s_3$:
-\begin{multline*}
-\operatorname*{\bigsymb{\bigvee}}_{p \in P} \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge  R_{23}\mpar{s_{2p}, s_{3}} \wedge	g_1 \wedge g_{2p} \wedge \operatorname*{\bigsymb{\bigvee}}_{y \in Y}\mpar{ \alpha_1 = \alpha_{3py} \wedge g_{3py}}}
-%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2p}} \beta_{1j} = \beta_{2pj} 
-\implies \hspace{6cm}\\
-%\exists
-%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
-\bigsymb{\bigwedge_{x\in X}}
-\operatorname*{\bigsymb{\bigvee}}_{p \in P}\operatorname*{\bigsymb{\bigvee}}_{y \in Y} 
-\mpar{\everymath{\displaystyle}\begin{array}{l}		
-\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_{2p} \land \bigwedge_\subbox{j \in J'_{2p}} \beta_{2pj} = \beta_{1xj} \land  \bigwedge_\subbox{j \in J'_{3py} \cap H} \beta_{2pj}=\beta_{3pyj} \\ g_{1 x}  \land
- R_{12}\mpar{s'_{1 x}, s'_{2p}} \wedge R_{23}\mpar{s'_{2p}, s'_{3y}} \psubst{\psi_{1 x} \uplus \psi_{2p}\uplus \psi_{3py}}
- \end{array}}
-\end{multline*}
-
---------------------------------------
-
-Firstly, according to the refinement relation between  $A_1$ and $A_2$ we have:
-\begin{multline*}
-\bigforall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_2} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\ 
-\bigsymb{\bigexists} 
-\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},
- V_1 \uplus V_2 \uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R_{12}\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 
-%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} 
-\implies \hspace{6cm}\\
-%\exists
-%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
-\bigsymb{\bigwedge_{x\in X}}
-\mpar{
-\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_2 \land \bigwedge_\subbox{j \in J'_2 } \beta_{2j} = \beta_{1xj}\land g_{1 x}\land
- R_{12}\mpar{s'_{1 x}, s'_2}\psubst{\psi_{1 x} \uplus \psi_2}}
-\end{multline*}
-Yet according to the refinement  relation between   $A_2$ and $A_3$ and Definition \ref{Def:OA-Refinement} we have:
-
-\begin{multline*}
-\bigforall \mpar{s_2, s_3} \in S_1 \times S_3, \bigsymb{\forall} \mpar{t_2, t_3} = \mpar{\OTx{2}{}{2}{2}, \OTx{3}{}{3}{3}} \in \fOT{s_2} \times \fOT{s_3} \\ 
-\bigsymb{\bigexists} 
-\mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X},
-V_2 \uplus V_3\uplus \biguplus_{x\in X}\fvars{t_{2x}} \uplus \fvars{t_3} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R_{23}\mpar{s_2, s_3} \wedge 	g_2 \wedge g_3 \wedge \alpha_2 = \alpha_3 
-%\wedge \bigwedge_\subbox{j \in J'_2 \cap J'_3} \beta_{2j} = \beta_{3j} 
-\implies \hspace{6cm}\\
-%\exists
-%\OTx{1}{a}{3}{3}\in \fOT{s_2}. \\
-\bigsymb{\bigwedge_{x\in X}}
-\mpar{
-\alpha_2=\alpha_{2 x}  \land J'_{2x}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{2xj}\land g_{2 x}\land
- R_{23}\mpar{s'_{2 x}, s'_3}\psubst{\psi_{2 x} \uplus \psi_3}}\\
-\end{multline*}
 
@@
 $\forall \mpar{s_1,s_3} \in S_1 \times S_3$ and\\ $\bigsymb{\forall} \mpar{t_1, t_{3}}\!=\! \mpar{\OTx{1}{}{1}{1},\OTx{3}{}{3}{3}}\! \in\! \fOT{s_1} \times \fOT{s_3}$
-\begin{multline*}
-\bigsymb{\bigexists} 
-\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},\\
- V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1} \uplus \fvars{t_2} \uplus \fvars{t_3} \uplus \biguplus_{x\in X}\fvars{t_{1x}}     \vdash \hspace{6cm}\\  R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \wedge 	g_1 \wedge g_2 \wedge   g_3\wedge  \alpha_1 = \alpha_2  \wedge \alpha_2 = \alpha_3
-%\wedge \bigwedge_\subbox{j \in J'_2 \cap J'_3} \beta_{2j} = \beta_{3j}} 
-%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} 
-\implies \hspace{6cm}\\
-%\exists
-%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
-\bigsymb{\bigwedge_{x\in X}}
-\mpar{
-\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_2 \land \bigwedge_\subbox{j \in J'_2 } \beta_{2j} = \beta_{1xj}\land g_{1 x}\land
- R_{12}\mpar{s'_{1 x}, s'_2}\psubst{\psi_{1 x} \uplus \psi_2}} \wedge\\ R_{23}\mpar{s'_{2}, s'_3}\psubst{\psi_{2} \uplus \psi_3}\hspace{6cm}\\
-\end{multline*}
+
 By rearranging, simplifying and removing the variables of $A_2$ that have not effect on   $A_1$ et  $A_3$, we get the desired result.

### 2022-08-18 2021-Refinement/paper/refinementarticle.tex
adding reference

@@
 
+\TODO{Simulation: Il y a differentes facons de voir le relation de reffinement entre l'implem et la spec:
+\begin{itemize}
+\item implem as a conformance of spec:  implem deadlocks less often.
+\item implem as a (nondeterminism) reduction of spec:  implem deadlocks less often. Can only used be used for complete specification.
+\item implem as an extension of spec. C'est le complement du raffinement par reduction, i.e. Can be used to complete partial specification (implem can exhibit more behaviour than spec).
+Our definition of simulation matches the definition given in \cite{EshuisF:2002} Section 3.2 $\implies$ Refinement par extension according to Thm 8 (Section 4)
+\end{itemize}
+}
+
 Note in this definition, instead of matching an instantiated transition (with all variables assigned) of the first automata to another instantiated transition of the second, it matches an open transition $t_1$ to a family of covering open transitions $t_{2x}^{x\in X}$.

### 2022-09-01 2021-Refinement/paper/refinementarticle.tex
FACS proofs

@@
 %\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
-\bigsymb{\bigwedge_{x\in X}}
+\bigsymb{\bigvee_{x\in X}}
 \mpar{
@@
 
+Consider $(t_1,t_3)\in\fOT{s_1} \times \fOT{s_3}$
+
 \newpage
 \TODO{[RABEA] proof}
-Let's consider any $s_{2p} \in (s_{2p})^{p\in P}$. According to the refinement relation between  $A_1$ and $A_2$, we have  the following formula that we denote ($*$):\\
-for any open transition $t_1$ in $T_1$  originating from $s_1$:
+Let's consider any $s_{2p} \in (s_{2p})^{p\in P}$. Consider  $t_1$ in $T_1$  originating from $s_1$:
 \begin{align*}
@@
 \end{align*}
-there exists an indexed family of OTs originating from $s_{2p}$: 
+According to the refinement relation between  $A_1$ and $A_2$ there exists an indexed family of OTs originating from $s_{2p}$: 
 \begin{align*}
@@
 such that $\forall x \in X, J'_{2px} \cap H = J'_1 \cap H$ and
-\begin{multline*}
+\begin{multline}\label{lab1}\tag{$*$}
 %\everymath{\displaystyle}
@@
 		\end{array}}} 
-\end{multline*}	
-On the other hand, according to the refinement relation between   $A_2$ and $A_3$, we know condition 3 is satisfied, $\bigforall \mpar{s_{2p}, s_3} \in S_1 \times S_3$ and $\bigsymb{\forall} \mpar{t_{2p}, t_3} \in \fOT{s_{2p}} \times \fOT{s_3}$ and in particular for  the set $(t_{2px})^{x\in X_p}$ so we  have the following that we denote ($**$):
+\end{multline}	
+On the other hand, according to the refinement relation between   $A_2$ and $A_3$, we know condition 3 is satisfied, $\bigforall \mpar{s_{2p}, s_3} \in S_2 \times S_3$ and $\bigsymb{\forall} \mpar{t_{2p}, t_3} \in \fOT{s_{2p}} \times \fOT{s_3}$ and in particular for  the set $(t_{2px})^{x\in X_p}$ so we  have the following that we denote ($**$):
 \begin{multline*}
@@
 %\OTx{1}{a}{3}{3}\in \fOT{s_2}. \\
-\bigsymb{\bigwedge_{y\in Y_X}}
+\bigsymb{\bigvee_{y\in Y_X}}
 \mpar{
@@
 \end{multline*}
+combining $(*)$ and $(**)$ with the definition of the set $s_{2p}$, we obtain (variables on the left  of the $\vdash$ omitted for readability)
+\begin{align*}
+ R_{13}\mpar{s_1, s_3} &\wedge 	g_1 \wedge g_3 \wedge \alpha_1 = \alpha_3 \implies \\
+&(\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}) \wedge 	g_1 \wedge g_3 \wedge \alpha_1 = \alpha_3  \implies \\
+& (\bigvee_{{p\in P}}{\bigsymb{\bigvee}}_{x \in X_p} \left(\mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_1 = \alpha_{2px}= \alpha_3 \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \nwedge\\
+			 g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}}
+		\end{array}} \right) 
+	\wedge R_{23}\mpar{s_{2p},s_3}  \wedge g_3  \implies \\
+\end{align*}
+
 Again according to the refinement  relation between  $A_1$ and $A_2$ and condition 3  the following is satisfied $\bigforall \mpar{s_1, s_{2p}} \in S_1 \times S_2$ , in particular over the family of transitions in $(t_{2pxy})^{y\in Y_X}$:

### 2022-09-27 2016-Weak-FH-Bisim/WeakBisim.tex
Submission weak bisim + work on the refinement paper (body)
advancing on remarks

@@
 
-\title{Compositional equivalences based on Open pNets
+\title{Compositional Equivalences Based on Open pNets
 %\thanks{This work was partially funded by the Associated Team FM4CPS
@@
 
-\author{Ludovic Henrio}
+\author{Ludovic Henrio\corref{cor1}}
 \address{Univ Lyon, EnsL, UCBL, CNRS, Inria,  LIP, F-69342, LYON Cedex 07, France.}
@@
 
+\cortext[cor1]{Corresponding author}
 \begin{abstract}
@@
 placeholders inside the hierarchical structure  that can be filled later by sub-systems.
-However, there is no standard tool for defining the semantics of an open system in this context, this article first defines \emph{open automata} that are labelled transition systems with parameters and holes.
-
-Relying on open automata, this article defines bisimulation relations  for the comparison of systems specified as pNets.
- We first define a strong bisimulation for open pNets.
-  We then define an equivalence relation similar to
-  the classical \emph{weak bisimulation}, and study its properties.
-Among these properties we are interested in compositionality: if two systems are proven equivalent they will be undistinguishable by their context, and they will also be undistinguishable when their holes are filled with equivalent systems.
+However, there is no standard tool for defining the semantics of an open system in this context.
+This article first defines \emph{open automata} that are labelled transition systems with parameters and holes.
+Relying on open automata, it then defines bisimulation relations  for the comparison of systems specified as pNets.
+ We first present a strong bisimulation for open pNets.
+Next we offer an equivalence relation similar to
+  the classical \emph{weak bisimulation} equivalence, and study its properties.
+Among these properties we are interested in compositionality: if two systems are proven equivalent they will be undistinguishable by their context, and they will also be indistinguishable when their holes are filled with equivalent systems.
 We identify sufficient conditions to ensure compositionality of strong and weak bisimulation.
-The article is illustrated with a transport protocol running example.
+The contributions of this article are illustrated using a transport protocol as running example.
 \end{abstract}
+
+\begin{keyword}
+Bisimulation, compositionality, automata, semantics.
+\end{keyword}
 
@@
 transitions~\cite{deSimone85,Larsen87}. 
-These works use the term \emph{parameter} to designate systems where variables that have a strong influence the system structure and behaviour.
+These works use the term \emph{parameter} to designate  variables whose value have a strong influence the system structure and behaviour.
 In parameterised systems, parameters can typically be the number of processes in the system or the way they interact.
@@
 bisimulations (early and late, strong and weak, and their congruent versions). They also extended this work to models with explicit assignments \cite{Linconcur96}.
-Separately J. Rathke~\cite{HennessyRathke:TCS98} defined another symbolic semantics for 
+Separately Rathke~\cite{HennessyRathke:TCS98} defined another symbolic semantics for 
 a parameterised broadcast calculus, together with strong and weak bisimulation
 equivalences, and developed a symbolic model-checker based on a tableau
-method for these processes. 30 years later, no
-practical verification approach and no verification platform are
-using this kind of approaches to provide proof methods for
-value-passing processes or open process expressions.
+method for these processes. Thirty years later, no
+practical verification method and no verification platform use this kind of approaches to provide proof methods for value-passing processes or open process expressions.
 
 This article provides a theoretical background that allows us to implement such a verification 
-platform. We build upon the concept of pNets that allowed us to give a behavioural semantics 
+platform. We build upon the concept of pNets that we have employed to give a behavioural semantics 
 of distributed components and verify the correctness of distributed applications in the past 15 years. pNets  is a
@@
 classes of distributed languages, and as a common internal format for
-our tools.  pNets allow the
+our tools.  pNets support the
 specification of parameterised hierarchical labelled
@@
 by any correct instantiation of the holes.
-As a consequence, our model allows us to reason on composition
-operators as well as on full-size distributed systems. The parametric
-nature of the model and the properties of compositionability of the
+As a consequence, our model allows us to reason about composition
+operators as well as about realistic distributed systems. The parametric
+nature of the model and the properties of compositionality of the
 equivalence relations are thus  the main
@@
 
-\paragraph{A semantics for Open pNets based on open automata}
+\paragraph{A semantics for open pNets based on open automata}
 The semantics of pNets can be expressed as a translation to a labelled transition system, but only if the pNet has no parameter and no hole.
@@
 
-\subsubsection*{Previous Works and Contribution}
+\subsubsection*{Previous works and contribution}
 While most of our previous works relied on closed, fully-instantiated semantics~\cite{BBCHM:article2008,AmeurBoulifa2017,HKM-FASE16}, it is only recently that we could design a first version of a  parameterised semantics for pNets with a strong bisimulation equivalence~\cite{henrio:Forte2016}.
@@
 
-\section{Background and notations}\label{sec:notations}
+\section{Background and Notations}\label{sec:notations}
 This section introduces the notations we will use in this article, and  recalls the definition of pNets~\cite{henrio:Forte2016} with an informal semantics  of the pNet constructs.
@@
 
-\subsection{Parameterised Networks (pNets)}
-\label{section:pnets}
+\subsection{The principles of Parameterised Networks (pNets)}
+\label{section:pnets-princ}
 
@@
 
+We introduce the notion of pNets through a simple example below, and define formally pLTSs and pNets afterwards:
+
+\begin{example}[CCS choice]\label{ex:CCSplus}
+
+Here is the encoding of a choice operator.\\[1.5ex]
+\noindent\begin{tabular}{cp{.45\linewidth}}
+ \begin{minipage}{.49\linewidth}
+ \includegraphics[width=1.0\linewidth]{XFIG/Choice.pdf}\vspace{-10ex}
+\end{minipage} 
+&
+ It consists of one pNet with two holes and a sub-net. The left hole is
+  indexed $L$ the right hole $R$. The sub-net is an labelled transition system (LTS) with three states and emitting actions $l$ and $r$. 
+\\
+\end{tabular}
+
+The behaviour of the pNet is defined with 
+  synchronisation vectors also shown on the figure.
+In the examples, we write them on the form $<a,-,l>\to a$.
+This states that if the first hole $L$ performs the action $a$ and the third sub-net, i.e.
+the LTS, performs the action $l$, both of them progress synchronously, and an action $a$ is emitted by the pNet.
+$-$ denotes that the second hole does nothing.
+On the formal side, numbering and ordering the vectors is cumbersome, this is why we adopt indexed families of actions.
+When encoding this operator, the LTS is sometimes called the ``control part'', it controls the evolution of the rest of the pNet. 
+The first action  of one of  the holes decides which branch of the LTS is activated;
+   all subsequent actions will be from the same side.
+
+\end{example}
 %\LUDO{introduce magic op}
@@
 %$a$ is not already an indexed set.}
+
+\subsection{Parameterised Labelled Transition systems (pLTS)}
+\label{section:plts}
 
@@
 
+\subsection{Parameterised Networks (pNets)}
+\label{section:pnets}
+
 Now we define
@@
 
-\begin{definition}[Sorts, Holes, Leaves, Variables of pNets]\label{def-sortholeleave}~~
+\begin{definition}[Sorts, holes, leaves, variables of pNets]\label{def-sortholeleave}~~
 
@@
 % a bisimulation
-an equivalence between the semantics presented in this article and the operational one shown in~\cite{AmeurBoulifa2017} is outside the scope of this article because we focus here on the modelisation of holes that were not modelled in the previous semantics.
-
-\subsection{Running Example}
+an equivalence between the semantics presented in this article and the operational one shown in~\cite{AmeurBoulifa2017} is outside the scope of this article because we focus here on the modelling of holes that were not considered in the previous semantics.
+\TODO{Check}
+It is however easy to see that, in case there is no hole the structure of the open automaton that defines the semantics here is very close to the pLTS that is used in~\cite{AmeurBoulifa2017} to define the semantics even though the formalisms are different.
+
+\subsection{Running example}
 To illustrate this work, we use a simple communication protocol, that provides safe transport of data between two processes, over unsafe media.
@@
 
-\subsection{Open Automata}
+\subsection{Open automata}
  Open automata (OA) are not composition structures but they are made of transitions that are dependent of the actions of the holes, and they can reason on a set of variables (potentially with only symbolic values).
@@
 
+\TODO{Check this paragraph}
 It is important to understand the difference between the red dotted rule and a classical 
 inference rule. They correspond to two different logical levels.
-On one side, classical (black) inference rules  use  an expressive logic (like any other computer science article).
- On the other side, open transition rules (with dotted lines) are logical implications, but using a  logic with a specific syntax and that can be mechanized (this logic includes the boolean expressions $\AlgB$, boolean operators, and term equality).
+On one side, classical (black) inference rules act at the mathematical level of the paper proofs. They use  an expressive logic (like any other computer science article).
+ On the other side, open transition rules (with dotted lines) are logical implications that belong to the open automata algebra.
+Their  logic has a specific syntax  that can be mechanized; this logic includes the boolean expressions $\AlgB$, boolean operators, and term equality.
 %  Open transitions could typically be handled in a 
@@
 
-\begin{thm}[FH-Bisimulation is an equivalence]\label{thm-equiv} Suppose $\mathcal{R}$ 
+\begin{thm}[FH-bisimulation is an equivalence]\label{thm-equiv} Suppose $\mathcal{R}$ 
 is an FH-bisimulation. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
@@
 
-\begin{example}[CCS choice (counter-example)]\label{ex:CCSplus}
-Here is the encoding of a choice operator.\\[1.5ex]
-\begin{tabular}{cp{.53\linewidth}}
- \begin{minipage}{.4\linewidth}
- \includegraphics[width=1.04\linewidth]{XFIG/Choice.pdf}\vspace{-18ex}
-\end{minipage} 
-&
-The left hole is
-  indexed $l$ the right hole $r$. The third subnet, contains an LTS encoding
-  the control part. We obtain the specific behaviour with the 
-  synchronisation vector. The first action  of one of
-  the holes decides which branch of the LTS is activated;
-   all subsequent actions will be from the same side. 
-\\
-\end{tabular}
-
-This pNet does not satisfy Definition~\ref{def:non-obspNet}. Indeed, if $a$ or $b$ is $\tau$ then the $+$ operator can indeed observe the $\tau$ transition.
-On the other side, the parallel operator defined similarly \emph{satisfies} Definition~\ref{def:non-obspNet}.
-
-\end{example}
-
 With this definition, it is easy to check that the open automaton that gives the semantics of such an open pNet cannot observe silent actions in the sense of Definition~\ref{def:Non-ObsTau}.
@@
 \begin{example}[CCS Choice] Consider the $+$ operator of CCS, shown in  Example~\ref{ex:CCSplus}. 
-It is well-known that weak bisimulation is not a congruence in CCS, and this is reflected here because we have shown that the $+$ operator can observe the $\tau$ transitions.
+The pNet does not satisfy Definition~\ref{def:non-obspNet}. Indeed, if $a$ or $b$ is $\tau$ then the $+$ operator can  observe the $\tau$ transition.
+It is well-known that weak bisimulation is not a congruence in CCS, this corresponds to the fact that the $+$ operator can observe the $\tau$ transitions.
 Thus, even if we can define a weak bisimulation for CCS with $+$ it does not verify the necessary requirements for being a congruence.
+
+On the other side, the parallel operator defined similarly \emph{satisfies} Definition~\ref{def:non-obspNet}, and indeed bisimilarity is a congruence for the parallel operator in CCS.
 \end{example}
@@
 
-\subsubsection*{Open and Compositional systems}
+\subsubsection*{Open and compositional systems}
 %\TODO{retravailler le paragraphe ci dessous: faire ref a Facs-2013 (reconfig ds pNets) - virer 14 (probabilistic) ?} \cite{GasparHM:2013}
@@
 
-\section{Conclusion and Discussion}
+\section{Conclusion and discussion}
 \label{section:conclusion}

### 2022-09-27 2016-Weak-FH-Bisim/WeakBisim.tex
example

@@
 pNet is a convenient model to model concurrent systems in a hierarchical and parameterised way.
-The coordination between processes is expressed as synchronisation vectors that allow the definition of complex and expressive synchronisation patterns.
-Open pNets are pNets for which some elements in the hierarchy are still undefined, such undefined elements are called \emph{holes}; a hole can be \emph{filled} later by providing another pNet.
+The coordination between processes is expressed as synchronisation vectors that allow for the definition of complex and expressive synchronisation patterns.
+Open pNets are pNets for which some elements in the hierarchy are still undefined, such undefined elements are called \emph{holes}. A hole can be \emph{filled} later by providing another pNet.
 This article first defines pNets and illustrates with an example how they can be used to provide the model of a communicating system.
@@
 \paragraph{A semantics for open pNets based on open automata}
-The semantics of pNets can be expressed as a translation to a labelled transition system, but only if the pNet has no parameter and no hole.
-Adding parameters to a LTS is quite standard but enabling holes inside LTSs is not a well-defined notion.
+The semantics of pNets can be expressed as a translation to a labelled transition system (LTS), but only if the pNet has no parameter and no hole.
+Adding parameters to a LTS is quite standard but enabling holes inside LTSs is not a standard notion.
 
@@
 holes that can be filled by processes.
-We call such LTSs with parameters and holes and equiped with a composition operation, \emph{open automata}.
-The main goal of this article is to define the theory behind open automata and to use them to provide a semantics and prove composition properties for open pNets.
-  The transitions of open automata are much more complex than transitions of an LTS as the firing on a transition depends on parameters and actions that are symbolic.
-This article defines the notion of \emph{open transition} a transition that is symbolic in terms of parameters and coordinated actions.
+We call such LTSs with parameters and holes \emph{open automata}.
+The main goal of this article is to define the theory behind open automata and to use them to provide a semantics and prove compositionality properties for open pNets.
+  The transitions of open automata are much more complex than transitions of an LTS as the firing of a transition depends on parameters and actions that are symbolic.
+This article defines the notion of \emph{open transition}, namely a transition that is symbolic in terms of parameters and coordinated actions.
 
@@
 the LTS, performs the action $l$, both of them progress synchronously, and an action $a$ is emitted by the pNet.
-$-$ denotes that the second hole does nothing.
+The symbol $-$ at the second position denotes that the second hole does nothing.
 On the formal side, numbering and ordering the vectors is cumbersome, this is why we adopt indexed families of actions.
-When encoding this operator, the LTS is sometimes called the ``control part'', it controls the evolution of the rest of the pNet. 
+The LTS is sometimes called the ``control part'', it controls the evolution of the rest of the pNet. 
 The first action  of one of  the holes decides which branch of the LTS is activated;
-   all subsequent actions will be from the same side.
+   all subsequent actions will be performed by the same side.
 

### 2022-09-27 2016-Weak-FH-Bisim/WeakBisim.tex

@@
 
-Contrarily to pNets, open automata are not hierarchical structures, we consider them here as a mathematical structure convenient for formal reasoning but not adapted to the definition of a complex and structured system.
+UNlike pNets, open automata are not hierarchical structures, we consider them here as a mathematical structure that is convenient for formal reasoning but not adapted to the definition of a complex and structured system.
 Open transitions are expressed in terms of logics while the communication in pNets is specified as synchronisation vectors that specify synchronised actions.
-Open automata could alternatively be  seen as an algebra that can be studied independently from its application to pNets but their composition properties make more sense in a hierarchical model like pNets.
+Open automata could alternatively be  seen as an algebra that can be studied independently from its application to pNets but their compositionality properties make more sense in a hierarchical model like pNets.
 
@@
 It also adds a notion of global state to automata.
-Also, in \cite{henrio:Forte2016} the study of compositionability was only partial, and in particular the proof that bisimulation is an equivalence is one new contribution of this article and provides a particularly interesting insight on the semantic model we use.
+Moreover, in \cite{henrio:Forte2016} the study of compositionality was only partial, and in particular the proof that bisimularity is an equivalence is one new contribution of this article and provides a particularly interesting insight on the semantic model we use.
 The new formalism allowed us to extend the work and define weak bisimulation  for open automata, which is entirely new.
-This allows us to define a weak bisimulation equivalence for open pNets with valuable properties of compositionality.
+This allows us to define a weak bisimulation equivalence for open pNets with valuable compositionality properties.
 To summarise, the contribution of this paper are the following:
@@
 \item The definition of open automata: an algebra of parameterised automata with holes, and a strong bisimulation equivalence.
-This is an adaptation of~\cite{henrio:Forte2016} with an additional property stating that strong bisimulation equivalence is indeed an equivalence relation.
+This is an adaptation of~\cite{henrio:Forte2016} with an additional result stating that strong bisimulation equivalence is indeed an equivalence relation.
 \item A semantics for open pNets expressed as translation to open automata. This is an adaptation of~\cite{henrio:Forte2016} with a complete proof that strong bisimulation is compositional.
-\item A theory of weak bisimulation for open automata, and its properties.
+\item A theory of weak bisimulation for open automata, and a study of its properties.
 It relies on the definition of weak open transitions that are derived from transitions of the open automaton by concatenating invisible action transitions with one (visible or not) action transition.
@@
 Classical bisimulations require to exhibit, for each transition of one system, a transition of the other system that simulates it.
-Instead, bisimulation for open automata  relies on the simulation of each open transition of one automaton by a set of open transitions of the other one, that should cover all the
+Instead, bisimulation for open automata  relies on the simulation of each open transition of one automaton by \emph{a set of} open transitions of the other one, that should cover all the
 cases where the original transition can be triggered.
 
-Compositionality of bisimulation in our model come from the specification of the interactions, including actions of the holes.
+Compositionality of bisimulation in our model comes from the specification of the interactions, including actions of the holes.
 In pNets, synchronisation vectors define the possible interactions between the pNet that fills the hole and the surrounding pNets.
@@
 the semantics of open pNets expressed as open automata, and states
-compositional properties on the strong bisimulation for open
+compositionality properties of strong bisimularity for open
 pNets. 
@@
 equivalence on open automata and derives weak bisimilarity for pNets,
-together with properties on compositionality of weak bisimulation for
-open pNets. 
+together with compositionality properties  of weak bisimilarity. 
 Finally, Section~\ref{sec:RW} discusses related works and Section~\ref{section:conclusion} concludes the
@@
 This section introduces the notations we will use in this article, and  recalls the definition of pNets~\cite{henrio:Forte2016} with an informal semantics  of the pNet constructs.
-The only significant difference compared to our previous definitions is that we remove here the restriction that was stating that variables should be local to a state of a labelled transition system.
+The only significant difference compared to our previous definitions (from~\cite{henrio:Forte2016}) is that we remove here the restriction that was stating that variables should be local to a state of a labelled transition system.
 
@@
 %In general $x_i,y_i$ range over variables.
-\paragraph{Term algebra.}
-Our models rely on a notion of parameterised actions, that are
+\paragraph{Term algebra}
+Our models rely on a notion of parameterised actions, which are
 symbolic expressions using data types and variables. As our model aims
@@
 for denoting actions, nor any specific communication mechanism. So we
-leave unspecified the constructors of the algebra that will allow building
-expressions and actions. Moreover, we use a generic {\em action interaction}
+leave  the constructors of the algebra that will be used to build
+expressions and actions unspecified. Moreover, we use a generic {\em action interaction}
 mechanism, based on (some sort of) unification between two or more action
@@
 data expressions $\AlgE$, including a set of boolean
-expressions $\AlgE$ ($\AlgB\subseteq\AlgE$), 
+expressions $\AlgB$ ($\AlgB\subseteq\AlgE$), 
 and a set of action expressions $\AlgE$ called the action algebra
@@
 range over action labels, $\symb{op}$ be operators, and $x_i$ and $y_i$ range over
-variable names.
-
-We define two kinds of parameterised actions. The first kind distinguishes input variables and the second kind does not. 
+variable names. We additionally rely on a set of action names, ranged over by $a$, $b$, \ldots
+
+We define two kinds of parameterised actions.
+The first kind supports two kinds of parameters: input parameters that are variables and output parameters that can be any expression.
+The second kind makes no distinction between input and output parameters.
 The  actions that distinguish input variables will be used in the definition of \pLTS\ below and are defined as follows:
@@
 We additionally impose that each input variable does not
-appear somewhere else in the same action term:
+appear anywhere else in the same action term:
 $p_i=?x\Rightarrow\forall j\neq i.\, x\notin \vars(p_j)$.
 We define $iv(t)$  as the set of input variables of a term $t$ (without the '?' marker).
+Input variables are used in guards and to update the local state, they can only appear in well-identified expressions.
 Action algebras can encode naturally usual point-to-point message passing calculi (using 
-$a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs), but it also allows
+$a(?x_1,...,?x_n)$ for inputs, $a(v_1,..,v_n)$ for outputs), but they also allow
 for more general synchronisation mechanisms, like gate negotiation in Lotos, or broadcast
@@
 We use indexed sets in pNets because we want to consider a set of processes, and specify separately how to synchronise them.
-Roughly this could also be realised using tuples, however indexed sets are more general, can be infinite, and give a compact representation than using the position in a possibly long tuple.
+Roughly this could also be realised using tuples, however indexed sets are more general, can be infinite, and give a more compact representation than using the position in a possibly long tuple.
 
@@
 only a few entries we use the notation $(3\mapsto t_3)$ instead.
-In this article, sentences of the form ``there exists $t_i^{i\in I}$'' means there exists $I$ and a function that maps each element of $I$ to a term $t_i$.
+In this article, sentences of the form ``there exists $t_i^{i\in I}$'' means there exist $I$ and a function that maps each element of $I$ to a term $t_i$.
 %The operation  $A[j \mapsto a]$ updates the value associated to $j$ in map $A$ so that 
@@
 
-When this is not ambiguous, we shall use abusive notations 
+When this is not ambiguous, we shall abuse notations 
 %and notations 
@@
 To simplify equations, an indexed set can be denoted $\set{t}$
-instead of $t_i^{i\in I}$ when $I$ is irrelevant.
-
-The disjoint union on sets is $\uplus$. We extend it to  disjoint union  of indexed 
+instead of $t_i^{i\in I}$ when $I$ is irrelevant or clear from the context.
+
+The disjoint union on sets is $\uplus$ and we only use $A\uplus B$ when the index sets of the $A$ and $B$ are disjoints. We extend it to  disjoint union  of indexed 
 sets defined by the merge of the 
-two sets provided they are indexed on disjoint families.
+two sets provided they are indexed over disjoint families.
 The elements
@@
 %methods of different interfaces).
-The standard subtraction operation on indexed sets is $\setminus$, with $\dom(A\setminus B)=\dom(A)\setminus B$.
+The  subtraction operation on indexed sets is $\setminus$, it reduces the set of indexes such that $\dom(A\setminus B)=\dom(A)\setminus B$.
 
@@
 Note that we make no assumption on finiteness of the set of states nor
-on finite branching of the transition relation. Compared to our previous works~\cite{henrio:Forte2016,AmeurBoulifa2017} we extend the expressiveness of the model by making variables global.
+on finite branching of the transition relation. Compared to our previous works~\cite{henrio:Forte2016,AmeurBoulifa2017} make variables global, which makes the model easier to use.
 
@@
 \item[$\bullet$] $\to \subseteq S \times L \times S$ is the transition relation and 
-$L$ is the set of labels of the form:\\
+$L$ is the set of labels. Labels have the form:\\
 $\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in J}\rangle$,
 where $\alpha \in\AlgA$ is a parameterised action, $e_b \in
-\AlgB$ is a guard, and the variables $x_j$ 
+\AlgB$ is a guard, and the variables $x_j$ (that are pairwise distinct)
 are assigned the expressions $e_j\in \AlgE$.
@@
 		$\vars(\alpha)\backslash \iv(\alpha)\!\subseteq\! V$, 
-		$\vars(e_b)\!\subseteq\! \vars(s)\cup\vars(\alpha)$, and
+		$\vars(e_b)\!\subseteq\! V\cup\vars(\alpha)$, and
 		$\forall j\!\in\! J .\,\left(\vars(e_j)\!\subseteq\! V\cup\iv(\alpha)\land 

### 2022-09-27 2016-Weak-FH-Bisim/WeakBisim.tex
example

@@
  \begin{minipage}{.49\linewidth}
- \includegraphics[width=1.0\linewidth]{XFIG/Choice.pdf}\vspace{-10ex}
+ \includegraphics[width=1.0\linewidth]{XFIG/Choice.pdf}\vspace{-14ex}
 \end{minipage} 
 &
- It consists of one pNet with two holes and a sub-net. The left hole is
+ It consists of one pNet (Definition~\ref{def-pnets} below) with two holes and a sub-net.
+The pNet is represented by the top box with three circles and two synchronisation vectors on the right.
+The sub-net is a pLTS that is represented by the bottom box.
+\end{tabular}
+Each hole is represented by an empty disc, when the hole is filled it becomes a black disc.
+The left hole is
   indexed $L$ the right hole $R$. The sub-net is an labelled transition system (LTS) with three states and emitting actions $l$ and $r$.
-\\
-\end{tabular}
 
@@
 \begin{definition}[pNets]\label{def-pnets}
-A pNet $\pNet$ is a hierarchical structure where leaves are pLTSs and holes\\
+A pNet $\pNet$ is a hierarchical structure where leaves are pLTSs and holes \qquad
 $\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in 
-K}\myrangle$
+K}\myrangle$ \qquad
 where:
@@
 Synchronisation vectors are identified modulo renaming of variables that appear in their 
-action terms.
+action terms, e.g. the vectors $<a(x),b(x)>\to\tau$ and $<a(y),b(y)>\to\tau$ are equivalent.
 \end{definition}

### 2022-09-27 SujetStage/2022-pNetsubjectM2.tex
sujet stage

--- 2021-10-29 SujetStage/2021-pNetsubjectM2.tex
@@
 \begin{description}
-\item[\bf Main advisor:] Rabéa Ameur-Boulifa ?
-\item[\bf Co-advisors:] Ludovic Henrio and Eric Madelaine?
-\item[\bf Place:] Eurecom  -- Sophia Antipolis
+\item[\bf Advisors:] Rabéa Ameur-Boulifa\textsuperscript{(1)} and Ludovic Henrio\textsuperscript{(2)}
+\item[\bf Place:] ~\\(1) Eurecom  -- Sophia Antipolis
 \\
 or\\
-Laboratoire de l'Informatique du Parallélisme (LIP) --
-  \'Ecole Normale Supérieure de Lyon
+(2) Laboratoire de l'Informatique du Parallélisme (LIP) --
+  ENS de Lyon
+
+\item[contact:]  \quad \url{rabea.ameur-boulifa@telecom-paris.fr }  \quad \qquad \url{ludovic.henrio@ens-lyon.fr}
 \end{description}
@@
 
-\item  We additionally have defined a notion of refinement between open automata that would benefit from such behavioural types.
-One additional objective of the internship could be to improve the definition of refinement based on the notion of behavioural types that has been defined in the previous steps.
+\item  We additionally have defined a notion of bisimulation between open automata.
+One additional objective of the internship could be to prove that behavioural types behave well relatively to bisimilarity.
 
@@
 \end{itemize}
+
+The internship can be tackled only theoretically on paper, or formalised in an interactive theorem prover, or integrated with existing tools for open automata bisimilarity (based on SMT solvers).
 
@@
 \newblock {Compositional equivalences based on Open pNets}.
-\newblock arXiv {2007.10770} (2020).
+\newblock arXiv {2007.10770} (2021).
  \newblock \url{https://arxiv.org/abs/2007.10770}

### 2022-09-28 2016-Weak-FH-Bisim/WeakBisim.tex
sujet stage
progress on comments -> p13

@@
 Synchronisation vectors are identified modulo renaming of variables that appear in their 
-action terms, e.g. the vectors $<a(x),b(x)>\to\tau$ and $<a(y),b(y)>\to\tau$ are equivalent.
+action terms, e.g. the vectors $<a(x),b(x)>\to\tau$ and $<a(y),b(y)>\to\tau$ are equivalent. \TODO{check if more explanation is needed here}
 \end{definition}
@@
 \item
-The set of holes $\Holes(\pNet)$ of a pNet is the indices of the holes of the pNet 
+The set of holes $\Holes(\pNet)$ of a pNet is the set of indices of the holes of the pNet 
 itself plus the indices of all the holes of its sub-pNets.
-It is defined inductively (we suppose those indices 
+It is defined inductively (we suppose that those index sets are
 disjoints):
@@
 \Holes(\mylangle S,s_0,V, \to\myrangle) \!=\! \emptyset\\
-\Holes(\mylangle \pNet_i^{i\in I}\!,\set{\Sort}, \set{\symb{SV}}\myrangle) 
+\Holes(\mylangle \pNet_i^{i\in I}\!,\Sort_j^{j\in J}, \set{\symb{SV}}\myrangle) 
 =J\uplus{\displaystyle \bigcup_{i\in 
@@
 
+Note that  $\Holes(\pNet)$is a set of indexes because holes are characterized only by their indices, while entities at the leaves ar pLTSs and thus $\Leaves(\pNet)$ is a set of pLTSs.
 A pNet $Q$ is \emph{closed} if it has no hole: $\Holes(Q)=\emptyset$; else it
@@
 The actions on the \pLTS s can send or receive values, potentially modifying the value of variables.
-pNets are synchronisation entities: a pNet node composes several sub-pNets and  define how the sub-pNets interact, where a sub-pNet is either a pNet or a pLTS.
-The synchronisation between sub-pNets is defined by synchronisation vectors (originally introduced by \cite{Arnold1982}) that express how an action of a sub-pNet can be synchronised with actions of other sub-pNet, and how the resulting synchronised action is visible from outside of the pNet.
+pNets are synchronisation entities: a pNet node composes several sub-pNets and  defines how the sub-pNets interact, where a sub-pNet is either a pNet or a pLTS.
+The synchronisation between sub-pNets is defined by synchronisation vectors (originally introduced in \cite{Arnold1982}) that express how an action of a sub-pNet can be synchronised with actions of other sub-pNet, and how the resulting synchronised action is visible from outside of the pNet.
 The synchronisation mechanism is very expressive, including pattern-matching/unification between the parameterized actions within the vector, and an additional predicate over their variables.
 Consider a pNet node that assembles several pLTSs, the synchronisation vectors specify the way that transitions of the composed pNet are built from the transitions of the sub-nets.
-This can be seen as "conditional transitions" of the pNet, or alternatively, as a syntax to encode structural operational semantics (SOS rules) of the system: each vector expresses not only the actions emitted by the pNet but also what transitions of the composed pLTSs must occur to trigger this global transition.
+This can be seen as ``conditional transitions'' of the pNet, or alternatively, as a syntax to encode structural operational semantics (SOS rules) of the system: each vector expresses not only the actions emitted by the pNet but also what transitions of the composed pLTSs must occur to trigger this global transition.
 Synchronisation vectors can also express the exportation of an action of a sub-pNet to the next level, or to hide an interaction and make it non-observable.
@@
 
-pNets have been used to model GCM distributed component systems, illustrating the expressiveness of the model~\cite{AmeurBoulifa2017}. 
+pNets have been used to model distributed components using the Grid Component Model, illustrating the expressiveness of the model~\cite{AmeurBoulifa2017}. 
 These works show that pNets are convenient to express the behaviour of a system in a compositional way. 
-Unfortunately, the semantics of pNets and the existing tools at this point were only able to deal with a closed system completely instantiated: pNets could be used as composition operator in the definition of the semantics, which was sufficient to perform finite-state model checking on a closed system, but there was no theory for the use of pNets as operators and no tool for proving properties on open system.
+Unfortunately, the semantics of pNets and the existing tools at that point were only able to deal with a closed and completely instantiated system: pNets could be used as composition operators in the definition of the semantics, which was sufficient to perform finite-state model checking on a closed system, but there was no theory for the use of pNets as operators and no tool for proving properties on open system.
 Consequently, much of the formalisation efforts did not use holes and the interplay between holes, sorts, and synchronisation vector was not formalised.
-In previous works~\cite{AmeurBoulifa2017}, only closed pNets were equipped with a semantics, it was defined as labelled transition systems. 
+In previous works~\cite{AmeurBoulifa2017}, only closed pNets were equipped with a semantics, which was defined as labelled transition systems. 
 %The old semantics is not necessary to understand this article but it defines the semantics of pNets in a simpler and more operational setting. 
-The theory of pNets as operators able to fully take into account open systems is given in the following sections.
+The theory of pNets as operators for open systems is given in the following sections.
 Comparing formally the existing direct operational semantics and the semantics derived from open automata in the current article would be an interesting partial proof of soundness for our semantics.
@@
 argument, through the two protocol entities.
-Process $P$ sends an $\texttt{p-send(m)}$ message to the $\symb{Sender}$; this communication is denoted as $\texttt{\nounderline{in(m)}}$% , where underline actions represent internal actions that cannot be further synchronised with the environment, similarly to the $\tau$ of CCS.
+Process $P$ sends a $\texttt{p-send(m)}$ message to the $\symb{Sender}$; this communication is denoted as $\texttt{\nounderline{in(m)}}$% , where underline actions represent internal actions that cannot be further synchronised with the environment, similarly to the $\tau$ of CCS.
 In our formalisation we will also denote these actions $\tau$ for simplicity of notations but the examples are easier to read when invisible actions have significant names}
@@
 \subsection{Open automata}
- Open automata (OA) are not composition structures but they are made of transitions that are dependent of the actions of the holes, and they can reason on a set of variables (potentially with only symbolic values).
+ Open automata (OA) are not composition structures but they are made of transitions that are dependent of the actions of the holes, and they can use variables (potentially with only symbolic values). 
 %\TODO{adopt a uniform notation for open transitions, almost each instance has a 
@@
 	\end{mathpar}
-	Where $J'\subseteq J$ is the set of holes involved in the transition; $s, s'\in\mathcal{S}$ are states of the automaton; and $\beta_j$
-        is a transition of the hole $j$, with $\Sortop(\beta_j)\in\Sort_j$. $\alpha$  is the resulting action of this open transition.
+	where $J'\subseteq J$ is the set of holes involved in the transition; $s, s'\in\mathcal{S}$ are states of the automaton; and $\beta_j$
+        is a transition of the hole $j$, with $\Sortop(\beta_j)\subseteq\Sort_j$. $\alpha$  is the resulting action of this open transition.
 %        We call \emph{source variables} of an OT the union of all variables
@@
         \Pred\ is a predicate, \Post\ is a set of 
-	assignments that are effective after the open transition, they are
+	assignments that are effective after the open transition, and are
         represented as a substitution function: $({x_k\gets e_k})^{k\in K}$.
-Predicates and expressions of an open transition can refer to the variables in $V$, and
-        in the different terms
+Predicates and expressions of an open transition can refer to the variables inside  $V$ and the different terms
         $\beta_j$ and $\alpha$. More precisely:
-
 \begin{multline*}
@@
 
-An open automaton is  an automaton where each transition is an open transition.
+An open automaton is  an automaton where transitions are open transitions.
 \begin{definition}[Open automaton]
@@
 		\item[$\bullet$]   $J$ is a  set of indices.
-		\item[$\bullet$]   $\mathcal{S}$ is a set of states and $s_0$ an initial state
-		  among $\mathcal{S}$.
+		\item[$\bullet$]   $\mathcal{S}$ is a set of states and $s_0$ is an initial state
+		  belonging to $\mathcal{S}$.
 %       \item[$\bullet$] for each state $s$, $vars(s)=\{v_s\}$ is a set of state variables, 
@@
 
-While the definition and usage of the open transition can be formalised and taken in a pure syntactic acceptance, we take in this article a semantics and logical understanding of open automata. 
-Formally, the open transition sets in open automata are closed by a simple form of refinement that
-allows us to refine the predicate, or substitute any free variable by
-an expression. Formally, for all predicate $\Pred$ for all partial function $\Post$, if $V\!\cap \!\dom(\Post)=\emptyset$, we have: 
+While the definition and usage of the open transition can be considered purely syntactically, we take in this article a semantics and logical understanding of open automata. 
+We  see open transitions as logical formulas with a constrained syntax and logics rather than purely syntactical terms.
+Consequently, the open transition sets in open automata are closed by a simple form of refinement that allows us to refine the predicate, or substitute any free variable by
+an expression. Formally, for each predicate $\Pred$ for each partial function $\Post$, if $V\!\cap \!\dom(\Post)=\emptyset$, we have: 
 		 \begin{mathpar}

### 2022-09-28 2016-Weak-FH-Bisim/WeakBisim.tex

@@
 
-Another aspect of the logical interpretation of the
-formulas is that we make no distinction between the equality and the
-equivalence on boolean formulas, i.e. equivalence of two predicates
-$\Pred$ and $\Pred\,'$ can be denoted $\Pred=\Pred\,'$, where the $=$ symbol is not interpreted in a syntactical way.
+Another aspect of the semantic interpretation is that we consider terms up to semantic equivalence, i.e. equivalence of two predicates
+$\Pred$ and $\Pred\,'$ can be denoted $\Pred=\Pred\,'$, where the $=$ symbol is interpreted semantically.
 
@@
 
-The equivalence we need is a strong bisimulation between
-open automata having exactly the same holes (same indices and same sorts), but using a
-flexible matching 
-between open transitions, this will allow us to compare pNets
-with different architectures.
+%
+%The equivalence we need is a strong bisimulation between
+%open automata having exactly the same holes (same indices and same sorts), but using a
+%flexible matching 
+%between open transitions, this will allow us to compare pNets
+%with different architectures.
 
@@
 Consequently it would be too restrictive to impose that each transition of one automaton is matched by exactly one transition of the bisimilar automaton.
-Thus the definition of bisimulation requires that, for each open transition of one automaton, there exists a matching  set of open transitions covering the original one, indeed depending on the value of action parameters or automaton variables, different open transitions might simulate the same one.
+Thus the definition of bisimulation requires that, for each open transition of one automaton, there exists a matching  set of open transitions covering the original one.
+Indeed depending on the value of action parameters or automaton variables, different open transitions might simulate the same one.
 
@@
       if $\Pred_{s,t}$       is 
-      True, i.e. the states are related when the value of the automata variables% in $s$ and $t$
-  verify the predicate $\Pred_{s,t}$. 2) The free variables of  $\Pred_{s,t}$ belong to $V_1$ and $V_2$, i.e. $\vars(\Pred_{s,t})\subseteq V_1\cup V_2$.
+      True, i.e. the states are related when the value of the automata variables % in $s$ and $t$
+  satisfy the predicate $\Pred_{s,t}$. 2) The free variables of  $\Pred_{s,t}$ belong to $V_1$ and $V_2$, i.e. $\vars(\Pred_{s,t})\subseteq V_1\cup V_2$.
  FH-bisimulation is defined formally\footnote{In this article, we denote $\beta_{j x}$  a double indexed set, instead of the classical $\beta_{j,\, x}$.
@@
  Then 
-$\mathcal{R}$ is an FH-bisimulation if and only if for any  states
+$\mathcal{R}$ is an FH-bisimulation if and only if for all  states
 $s\in\mathcal{S}_1$ and $t\in\mathcal{S}_2$, $(s,t|\Pred_{s,t})\in\mathcal{R}$, we 

### 2022-09-29 2016-Weak-FH-Bisim/WeakBisim.tex
biblio

@@
 \subsubsection*{Previous works and contribution}
-While most of our previous works relied on closed, fully-instantiated semantics~\cite{BBCHM:article2008,AmeurBoulifa2017,HKM-FASE16}, it is only recently that we could design a first version of a  parameterised semantics for pNets with a strong bisimulation equivalence~\cite{henrio:Forte2016}.
+While most of our previous works relied on closed, fully-instantiated semantics~\cite{BBCHM:article2008,AmeurBoulifa2017,HenrioKSM:2016}, it is only recently that we could design a first version of a  parameterised semantics for pNets with a strong bisimulation equivalence~\cite{henrio:Forte2016}.
 This article builds upon this previous parameterised semantics and provides a clean and complete version of the semantics with a slightly simplified formalism that makes proofs easier.
@@
 Consider a pNet node that assembles several pLTSs, the synchronisation vectors specify the way that transitions of the composed pNet are built from the transitions of the sub-nets.
-This can be seen as ``conditional transitions'' of the pNet, or alternatively, as a syntax to encode structural operational semantics (SOS rules) of the system: each vector expresses not only the actions emitted by the pNet but also what transitions of the composed pLTSs must occur to trigger this global transition.
+This can be seen as ``conditional transitions'' of the pNet, or alternatively, as a syntax to encode structural operational semantics (SOS rules) \cite{deSimone85} of the system: each vector expresses not only the actions emitted by the pNet but also what transitions of the composed pLTSs must occur to trigger this global transition.
 Synchronisation vectors can also express the exportation of an action of a sub-pNet to the next level, or to hide an interaction and make it non-observable.
@@
 
-Weak symbolic bisimulation was introduced to relate transition systems
+Weak symbolic bisimulation \cite{HENNESSY:1995} was introduced to relate transition systems
 that have indistinguishable behaviour, with respect to some definition
@@
 The notion of non-observable actions varies in different contexts,
-e.g. $tau$ in CCS, and $i$ in Lotos, we could define classically a set of
+e.g. $tau$ in CCS \cite{Milner:1982,Milner:1989}, and $i$ in Lotos \cite{BOLOGNESI:1987}, we could define classically a set of
 \emph{internal/non-observable actions} depending on a specific action
@@
 are quite different from ours, in particular they are much less structured, and translating them is clearly outside the scope of this article.
-In previous work \cite{gaspar:hal-00916115}, we also have shown how (closed) pNet models could be used to encode and verify finite instances of reconfigurable component systems. 
+In previous work~\cite{GasparHM:2013}, we also have shown how (closed) pNet models could be used to encode and verify finite instances of reconfigurable component systems. 
 %Additionally, the more compositional constraint resolution provided by the authors could also be interesting to make our SMT proofs scale better (inside a single pNet for example), the integration of the Z3 framework described in \cite{Johnson:2014:qosa} with our proof theory for open pNets would also be worth investigating from a practical point of view.
@@
 There is also a clear relation with the seminal works on rule formats for Structured Operational Semantics, e.g.
-DeSimone format, GSOS, and conditional rules with or without negative premisses \cite{deSimone85,Bloom88bisimulationcant,GROOTE1992202,VANGLABBEEK2004229}.
+DeSimone format, GSOS, and conditional rules with or without negative premisses \cite{deSimone85,Bloom:1995,GROOTE1992202,VANGLABBEEK2004229}.
 The Open pNets model provides a way to define operators similar to these rules formats, but with quite different aim and approach.
@@
 and Buscemi et al.
-providing symbolic semantic and equivalence for different variants of pi calculus respectively \cite{borgstrom2004symbolic,delaune2007symbolic,liu2010complete,buscemi2008open}; and more recently
+providing symbolic semantic and equivalence for different variants of pi calculus respectively \cite{BorgstromBN04,DelauneKR:2007,LiuL:2010,BuscemiM:2008}; and more recently
  Feng et al. provide a symbolic bisimulation for quantum processes \cite{feng2014symbolic}.
@@
 Parameters are also crucial to reason on interaction protocols that can address one entity inside an indexed set of processes.
-pNets have been successfully used to represent behavioural specification of parallel and distributed components and verify their correctness~\cite{AmeurBoulifa2017,HKM-FASE16}.
+pNets have been successfully used to represent behavioural specification of parallel and distributed components and verify their correctness~\cite{AmeurBoulifa2017,HenrioKSM:2016}.
 VCE is the specification and verification platform that uses pNets as an intermediate representation.

### 2022-09-29 2016-Weak-FH-Bisim/WeakBisim.tex
minor

--- 2022-09-28 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
+Two open automata are FH-bisimilar if there exist an FH-bisimulation that relates their initial states.
+
 % \TODO{Eric: il reste des petits bugs genre $s^{2'}_x$ plutot que
@@
 $\Post_{OT_x}$ that are independent), applying the assignments of the involved rules.
-We can prove that such a bisimulation is an equivalence relation.
-
-\begin{thm}[FH-bisimulation is an equivalence]\label{thm-equiv} Suppose $\mathcal{R}$ 
-is an FH-bisimulation. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
+We can prove that  bisimilarity  is an equivalence relation.
+
+\begin{thm}[FH-bisimularity is an equivalence]\label{thm-equiv} FH-bisimilarity is 
 reflexive, symmetric and transitive.
@@
 
-\subsubsection*{Finite versus infinite open automata, and decidability:} 
+\subsubsection*{Finite versus infinite open automata, and decidability} 
 As mentioned in Definition \pageref{def:open-automaton}, we adopt here a semantic view on open automata. More precisely, in \cite{hou:hal-02406098}, we  define

### 2022-09-29 2016-Weak-FH-Bisim/WeakBisim.tex
vars

@@
 %actions, this set is named the \emph{sort}.
-Nodes of the tree (pNet nodes) are synchronising artefacts, using a
+Every node of the tree  is a pNet, it acts as a  synchronising artefacts, using a
 set of \emph{synchronisation vectors} that express the possible
@@
 \begin{definition}[pNets]\label{def-pnets}
-A pNet $\pNet$ is a hierarchical structure where leaves are pLTSs and holes \qquad
-$\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in 
-K}\myrangle$ \qquad
-where:
+A pNet $\pNet$ is a hierarchical structure where leaves are pLTSs and holes 
+\[
+\pNet\triangleq \pLTS~|~\mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, \symb{SV}_k^{k\in 
+K}\myrangle\]
+ We denote $\vars(P)$ the set of variables used by the pLTSs inside $P$ and $\Sort(P)$  the signature of the actions emitted by $P$; both are defined below, in Definition~\ref{def-sortholeleave}.
+A pNet is composed of the following:
 \begin{itemize}
-\item[$\bullet$] $I$ is a set of indices and $\pNet_i^{i\in I}$ is the family of sub-pNets indexed over $I$. $vars(P_i)$ and $vars(P_j)$ must be disjoint for $i\neq j$.
+\item[$\bullet$] $I$ is a set of indices and $\pNet_i^{i\in I}$ is the family of sub-pNets indexed over $I$. $\vars(P_i)$ and $\vars(P_j)$ must be disjoint for $i\neq j$.
 %  $\pNet_i^{i\in I}$ is a family of sub-pNets where $I\in\I_\P$ is the set over which sub-pNets are indexed.
@@
 
-\item The set of variables of a pNet $P$, denoted $vars(P)$ is disjoint union the set of variables of  all pLTSs that compose $P$.
+\item The set of variables of a pNet $P$, denoted $\vars(P)$ is disjoint union the set of variables of  all pLTSs that compose $P$.
 
@@
 To be precise, the state of each pLTS is entirely characterized by both the state of the automaton, and the value of its variables $V$.
-Consequently, the state of a pNet is not only characterized the tuple of pLTS states but also contains the value of its variables $vars(P)$.
+Consequently, the state of a pNet is not only characterized the tuple of pLTS states but also contains the value of its variables $\vars(P)$.
 

### 2022-09-29 2016-Weak-FH-Bisim/WeakBisim.tex
changes with fh - bisimilarity everywhere

@@
 This article first defines \emph{open automata} that are labelled transition systems with parameters and holes.
-Relying on open automata, it then defines bisimulation relations  for the comparison of systems specified as pNets.
- We first present a strong bisimulation for open pNets.
+Relying on open automata, it then defines bisimilarity relations  for the comparison of systems specified as pNets.
+ We first present a strong bisimilarity for open pNets called FH-bisimilarity.
 Next we offer an equivalence relation similar to
@@
 \begin{itemize}
-\item The definition of open automata: an algebra of parameterised automata with holes, and a strong bisimulation equivalence.
-This is an adaptation of~\cite{henrio:Forte2016} with an additional result stating that strong bisimulation equivalence is indeed an equivalence relation.
-\item A semantics for open pNets expressed as translation to open automata. This is an adaptation of~\cite{henrio:Forte2016} with a complete proof that strong bisimulation is compositional.
+\item The definition of open automata: an algebra of parameterised automata with holes, and a strong bisimulation relation.
+This is an adaptation of~\cite{henrio:Forte2016} with an additional result stating that strong FH-bisimilarity is indeed an equivalence relation.
+\item A semantics for open pNets expressed as translation to open automata. This is an adaptation of~\cite{henrio:Forte2016} with a complete proof that strong FH-bisimilarity is compositional.
 \item A theory of weak bisimulation for open automata, and a study of its properties.
@@
 The precise and sound definition of the concatenation is also a major contribution of this article.
-\item A resulting weak bisimulation equivalence for open pNets and a simple static condition on synchronisation vectors inside pNets that is sufficient to ensure that weak bisimulation is compositional.
-\item An illustrative example based on a simple transport protocol, showing the construction of the weak open transitions, and the proof of weak bisimulation.
+\item A resulting weak FH-bisimilarity equivalence for open pNets and a simple static condition on synchronisation vectors inside pNets that is sufficient to ensure that weak FH-bisimilarity is compositional.
+\item An illustrative example based on a simple transport protocol, showing the construction of the weak open transitions, and the proof of weak FH-bisimulation.
 \end{itemize}
@@
 
-Compositionality of bisimulation in our model comes from the specification of the interactions, including actions of the holes.
+Compositionality of bisimilarity in our model comes from the specification of the interactions, including actions of the holes.
 In pNets, synchronisation vectors define the possible interactions between the pNet that fills the hole and the surrounding pNets.
 In open automata, this is reflected by symbolic hypotheses that depend on the actions of the holes.
-This additional specification is the price to pay to obtain the compositionality of bisimulation that cannot be guaranteed in traditional process algebras.
-
-This approach also allows us to specify a sufficient condition on allowed transitions to make weak bisimulation compositional; namely it is not possible to synchronise on invisible actions from the holes or prevent them to occur.
+This additional specification is the price to pay to obtain the compositionality of bisimilarity that cannot be guaranteed in traditional process algebras.
+
+This approach also allows us to specify a sufficient condition on allowed transitions to make weak bisimilarity compositional; namely it is not possible to synchronise on invisible actions from the holes or prevent them to occur.
 
@@
 
+For example, the controller of Example~\ref{ex:CCSplus} has the sort $\{l,r\}$ and holes $\{L,R\}$.
 Note that  $\Holes(\pNet)$is a set of indexes because holes are characterized only by their indices, while entities at the leaves ar pLTSs and thus $\Leaves(\pNet)$ is a set of pLTSs.
@@
 %\LUDO{I added this paragraph}
-Because of the semantic interpretation of open automata, the set of open transition of an open automaton is infinite (for example because every free variable can be renamed).
-However an open automaton is characterized by a  subset of these open transitions which is sufficient to generate, by substitution the other ones.
-In the following, we will abusively write that we define an ``open automaton'' when we provide only the set of open transitions that is sufficient to generate a proper open automaton by saturating each open transition by all possible substitutions and refinements.
+Because of the semantic interpretation of open automata, the set of open transition of an open automaton is infinite (for example because every free variable can be substituted by any term).
+This raises an issue when a finite representation is needed, which is the case both in our tools, and when writing examples.
+When needed, we can rely on a \emph{canonical representation} of the open automaton, provided that a  finite subset of the open transitions  is sufficient to generate, by substitution, the other ones.
+Thus, we use this canonical representation  in our examples.
+In the following, we will abusively write that we define an ``open automaton'' when we provide its canonical representation.
 
@@
 equivalent states can trigger transitions with identical action labels.
-Its key characteristics are 1) the introduction of predicates in the bisimulation relation: the relation between states may depend on the value of the variables; 2) the bisimulation property relates elements of the open transitions and takes into account predicates over variables, actions of the holes, and state modifications.
+Its key characteristics are 1) the introduction of predicates in the bisimulation relation: the relation between states may depend on the value of the variables; 2)  bisimulation  relates elements of the open transitions and takes into account predicates over variables, actions of the holes, and state modifications.
  We name it FH-bisimulation,
@@
 \end{minipage}
- such that  $\forall x.\, J'=J_{x}$ and there exists $\Pred_{s',t_x}$ such that $(s',t_x|\Pred_{s',t_x})\in 
+ such that  $\forall x.\, J'=J_{x}$ and there exists some $\Pred_{s',t_x}$ such that $(s',t_x|\Pred_{s',t_x})\in 
  \mathcal{R}$
@@
 
-Two open automata are FH-bisimilar if there exist an FH-bisimulation that relates their initial states.
+Two open automata are FH-bisimilar if there exists an FH-bisimulation that relates their initial states\footnote{I.e., the predicate relation associated to the initial states is \True.}.
 
@@
 an alternative version of our bisimulation, called
-structural-FH-Bisimulation, based on structural open automata, and
-prove that the \emph{semantic} and \emph{structural} FH-Bisimulations coincide.
+structural FH-bisimulation, based on structural open automata, and
+prove that the \emph{semantic} and \emph{structural} FH-bisimulations coincide.
 In the sequel, all mentions of finite automata, and algorithms for
@@
 The definition of bisimulation for open automata allows us to derive  a
-bisimulation relation for open pNets. As pNets are composition
+bisimilarity relation for open pNets. As pNets are composition
 structures, it then makes sense to prove composition lemmas: we prove
@@
 \begin{definition}[FH-bisimulation for open pNets]\label{def:bisim-pnets}
-Two pNets are FH-bisimilar if there exists a relation between their associated 
-automata that is an FH-bisimulation and their initial states are in the relation (i.e. the predicate associated with the initial states is verifiable).
+Two pNets are FH-bisimilar if their associated open automata are bisimilar.
 %\TODO{check}
@@
 We can now prove that pNet composition  preserves
-FH-bisimulation. More precisely, one can define two preservation
+FH-bisimilarity. More precisely, one can define two preservation
 properties, namely 1) when one hole of a pNet is filled by two bisimilar other (open) pNets; and 2) when the same hole in two bisimilar pNets are
@@
 bisimilar contexts. The general case will be obtained by
-transitivity of the bisimulation relation (Theorem~\ref{thm-equiv}).
+transitivity of the bisimilarity relation (Theorem~\ref{thm-equiv}).
 
@@
 
-Two pNets are weak FH-bisimilar if there exists a relation between their associated 
-automata that is a weak FH-bisimulation and their initial states are in the relation, i.e. 
-the predicate associated to the relation between the initial states is \True.
+Two open automata are weak FH-bisimilar if there exists a weak FH-bisimulation relation that relates their initial states.
+Two pNets are weak FH-bisimilar if their associated open automata are weakly bisimilar.
  \end{definition}
@@
 
-\begin{thm}[Weak FH-Bisimulation is an equivalence]\label{thm-weak-equiv} Suppose $\mathcal{R}$ 
-is a weak FH-bisimulation. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
+\begin{thm}[Weak FH-bisimilarity is an equivalence]\label{thm-weak-equiv} Weak FH-bisimilarity is 
 reflexive, symmetric and transitive.
 \end{thm}
-The proof  is detailed in  \ref{app-WFH-equiv}, it follows a similar pattern as the proof that strong FH-bisimulation is an equivalence, but technical details are different, and in practice we rely on a variant of the definition of weak FH-bisimilarity; this equivalent version simulates a \emph{weak} open transition with a set of weak open transition.
-The careful use of the best definition of weak FH-bisimilarity makes the proof similar to the strong FH-bisimulation case.
+The proof  is detailed in  \ref{app-WFH-equiv}, it follows a similar pattern as the proof that strong FH-bisimilarity is an equivalence, but technical details are different, and in practice we rely on a variant of the definition of weak FH-bisimilarity; this equivalent version simulates a \emph{weak} open transition with a set of weak open transition.
+The careful use of the best definition of weak FH-bisimilarity makes the proof similar to the strong FH-bisimilarity case.
 
@@
 In practice, we are dealing with finite representations of the (infinite) open automata.
-In \cite{hou:hal-02406098}, we defined a slightly modified definition of the ``coverage'' proof obligation, in the case of strong FH-Bisimulation.
+In \cite{hou:hal-02406098}, we defined a slightly modified definition of the ``coverage'' proof obligation, in the case of strong FH-bisimulation.
 This modification is required to manage in a finite way all possible instantiations of an OT.
-In the case of weak FH-Bisimulation, the proof obligation from Definition \ref{def-Weak-bisim} becomes:
+In the case of weak FH-bisimulation, the proof obligation from Definition \ref{def-Weak-bisim} becomes:
 \begin{small}
@@
 where $fv_{OT}$ denotes the set of free variables of all expressions in $OT$.
-\subsection{Weak bisimulation for open pNets}
+\subsection{Weak FH-bisimilation for open pNets}
 
@@
 
-When silent actions cannot be observed, weak bisimulation is a congruence for open pNets: if $P$ and $Q$ are weakly bisimilar to $P'$ and $Q'$ then the composition of $P$ and $Q$ is weakly bisimilar to the composition of $P'$ and $Q'$, where composition is the hole replacement operator: 	$\pNet[\pNetQ]_{j}$ and
+When silent actions cannot be observed, weak FH-bisimilarity is a congruence for open pNets: if $P$ and $Q$ are weakly bisimilar to $P'$ and $Q'$ then the composition of $P$ and $Q$ is weakly bisimilar to the composition of $P'$ and $Q'$, where composition is the hole replacement operator: 	$\pNet[\pNetQ]_{j}$ and
 	$\pNet'[\pNetQ']_{j}$ are weak FH-bisimilar. This can be shown by proving the two following theorems.
@@
 
-\begin{thm}[Congruence for  weak bisimulation]\label{weak-thm-congr-eq}
+\begin{thm}[Congruence for  weak FH-bisimilarity]\label{weak-thm-congr-eq}
 	Consider an open pNet $P$
@@
 	ensured by 
-	weak bisimilarity.} 
+	weak FH-bisimilarity.} 
 	$\Sortop(\pNetQ)=\Sortop(\pNetQ')\subseteq\Sort_{j_0}$. Then 
@@
 
-\begin{thm}[Context equivalence for  weak bisimulation]\label{weak-thm-ctxt-eq}
+\begin{thm}[Context equivalence for  weak FH-bisimilarity]\label{weak-thm-ctxt-eq}
 	Consider two  open pNets
@@
 	J}, 	\set{\symb{SV'}}\myrangle$ that are weak FH-bisimilar
-	(recall they must have the same holes to be bisimilar) and that cannot observe silent actions.
+	(recall they must have the same holes to be FH-bisimilar) and that cannot observe silent actions.
 	Let $j_0\in J$ be a hole, and $\pNetQ$ be a pNet such that $\Sortop(\pNetQ)\subseteq\Sort_{j_0}$. Then 
@@
 
-\begin{thm}[Composability of weak bisimulation]\label{weak-compos}
+\begin{thm}[Composability of weak FH-bisimilarity]\label{weak-compos}
 	Consider two weak FH-bisimilar pNets with an arbitrary number of holes, such that the two pNets cannot observe silent actions. When replacing, 
@@
 The pNet does not satisfy Definition~\ref{def:non-obspNet}. Indeed, if $a$ or $b$ is $\tau$ then the $+$ operator can  observe the $\tau$ transition.
-It is well-known that weak bisimulation is not a congruence in CCS, this corresponds to the fact that the $+$ operator can observe the $\tau$ transitions.
-Thus, even if we can define a weak bisimulation for CCS with $+$ it does not verify the necessary requirements for being a congruence.
+It is well-known that weak bisimularity is not a congruence in CCS, this corresponds to the fact that the $+$ operator can observe the $\tau$ transitions.
+Thus, even if we can define a weak FH-bisimilarity for CCS with $+$ it does not verify the necessary requirements for being a congruence.
 
@@
 In Section~\ref{sec:weak} we have shown the full saturated weak automaton for both \symb{SimpleProtocolSpec} and \symb{SimpleProtocolImpl}.
-We will show here how we can check if some given relation between these two automata is a weak FH-Bisimulation.
+We will show here how we can check if some given relation between these two automata is a weak FH-bisimulation.
 
@@
   \medskip
-  Checking that $\mathcal{R}$ is a weak FH-Bisimulation means checking, for each of these triples, that each (strong) OT of one the states corresponds to a set of WOTs of the other, using the conditions from Definition \ref{def-Weak-bisim}.
+  Checking that $\mathcal{R}$ is a weak FH-bisimulation means checking, for each of these triples, that each (strong) OT of one the states corresponds to a set of WOTs of the other, using the conditions from Definition \ref{def-Weak-bisim}.
   We give here one  example: consider the second triple from the table, and transition $SS_3$ from state \texttt{b0}. Its easy to guess that it will correspond to $WI_3(0)$ of state $202$.
@@
 Open automata are somehow labelled transition systems with parameters and holes, a notion that is useful to define semantics, but makes less sense when modelling a system, compared to pNets.
-To be precise, it is on open automata that we define our bisimulation relations.
+To be precise, it is on open automata that we define our FH-bisimilarity relations.
 
 This article defines a strong and a weak bisimulation relation that are adapted to parameterised systems and hierarchical composition.
-Our bisimulation principle handles pNet parameters in the sense that two states might be or not in relation depending on the value of parameters.
-Our strong  bisimulation is compositional by nature in the sense that bisimulation is maintained when composing processes.
-We also identified a simple and realistic condition on the semantics of non-observable actions that allows weak bisimulation to be also compositional.
+Our FH-bisimulation principle handles pNet parameters in the sense that two states might be or not in relation depending on the value of parameters.
+Our strong  FH-bisimilarity is compositional by nature in the sense that FH-bisimilarity is maintained when composing processes.
+We also identified a simple and realistic condition on the semantics of non-observable actions that allows weak FH-bisimilarity to be also compositional.
 Overall we believe that this article paved the way for a solid theoretical foundation for compositional verification of parallel and distributed systems.
@@
 the relations with existing equivalences on both closed and open systems. In particular, our model being significantly different from those considered in \cite{IngolfsdottirL:2001}, it
-would be interesting to compare our "FH" family of bisimulations with the hierarchy of symbolic bisimulations from these authors.
+would be interesting to compare our ``FH'' family of bisimulations with the hierarchy of symbolic bisimulations from these authors.
 We also plan to apply open pNets to the study of complex composition
@@
 symbolic semantics in term of open automata \cite{QBMZ-AVOCS18}, and have
-developed algorithms to check strong FH-bisimulation \cite{hou:hal-02406098}.
-More recently we published preliminary work for the case of weak FH-Bisimulation \cite{}. 
+developed algorithms to check strong FH-bisimulation and weak FH-bisimulation \cite{hou:hal-02406098,PEPS}.
 The challenges here, in the context of our symbolic systems, is not so much algorithmic complexity,
@@
        	transitivity. 
-       	To prove transitivity of strong FH-bisimulation on pNets it is sufficient to 
+       	To prove transitivity of strong FH-bisimilarity on pNets it is sufficient to 
        	prove 
-       	transitivity of the strong FH-bisimulation on states. Consider 3 open automata 
+       	transitivity of the strong FH-bisimilarity on states. Consider 3 open automata 
        	$\mathcal{T}_1$, $\mathcal{T}_2$, $\mathcal{T}_3$ and states $s$, $t$, $u$ 
@@
 \subsection{Composition Lemmas}       
-       The proofs of the composition theorems for FH-bisimulation rely on two main lemmas,
+       The proofs of the composition theorems for FH-bisimilarity rely on two main lemmas,
 dealing respectively with the decomposition of a composed behaviour
@@
 
-       \section{Weak FH-bisimulation lemmas and proofs}
+       \section{Weak FH-bisimilarity lemmas and proofs}
 
@@
 
-\subsection{Weak bisimulation is an equivalence}\label{app-WFH-equiv}
+\subsection{Weak FH-bisimilarity is an equivalence}\label{app-WFH-equiv}
 
@@
 %\begin
-\noindent{\bf Theorem~\ref{thm-weak-equiv}}. \emph{Weak FH-Bisimulation is an equivalence}.
+\noindent{\bf Theorem~\ref{thm-weak-equiv}}. \emph{Weak FH-bisimilarity is an equivalence}.
  Suppose $\mathcal{R}$ 
@@
 
-With the above lemma, we can use the same technique as for Theorem \ref{thm-equiv}  to prove that a weak FH-bisimulation is an equivalence.
+With the above lemma, we can use the same technique as for Theorem \ref{thm-equiv}  to prove that a weak FH-bisimilarity is an equivalence.
 Indeed, we essentially use the same proof-scheme the main difference concerns  $\beta$ and  $\gamma$.
@@
 
-To prove weak FH-bisimulation of $\pNet[\pNetQ]_{j_0}$ and 
+To prove weak FH-bisimilarity of $\pNet[\pNetQ]_{j_0}$ and 
 	$\pNet[\pNetQ']_{j_0}$, we consider  an open transition $OT$ of $\pNet[\pNetQ]_{j_0}$, and an equivalent state of $\pNet[\pNetQ']_{j_0}$, and we try to find a family of WOT of 	$\pNet[\pNetQ']_{j_0}$ that simulates $OT$.
@@
 
-To prove weak FH-bisimulation of $\pNet[\pNetQ]_{j_0}$ and 
+To prove weak FH-bisimilarity of $\pNet[\pNetQ]_{j_0}$ and 
 	$\pNet'[\pNetQ]_{j_0}$, we consider  an open transition $OT$ of $\pNet[\pNetQ]_{j_0}$, and an equivalent state of $\pNet'[\pNetQ]_{j_0}$, and we try to find a family of WOT of 	$\pNet'[\pNetQ]_{j_0}$ that simulates $OT$.
@@
 \]
-Side conditions necessary to prove weak-FH bisimulations are:
+Side conditions necessary to prove weak FH-bisimulations are:
 \[\forall x.\, (S'_P\uplus S'_Q,S'_{P' x}\uplus S'_Q, \Pred_{P,P' x})\in\mathcal{R}\]
@@
 
-        \subsection{Details of the Bisimulation Checking}
-
-We recall here the relation $\mathcal{R}$ that is the candidate for our weak bisimulation relation:
+        \subsection{Details of the FH-bisimulation checking}
+
+We recall here the relation $\mathcal{R}$ that is the candidate for our weak FH-bisimulation relation:
 
@@
 
-         Note that if we were using the alternative weak bisimulation relation from Appendix \ref{app-WFH-equiv}, Lemma \ref{lem-rel-OT-WOT}, that is checking strong bisimulation between the corresponding
+         Note that if we were using the alternative weak FH-bisimulation relation from Appendix \ref{app-WFH-equiv}, Lemma \ref{lem-rel-OT-WOT}, that is checking strong FH-bisimulation between the corresponding
 weak automaton, we would have a more transitions coverage to examine, as we have 4 weak transitions for $b0$ in the \symb{SimpleProtocolSpec} weak automaton, and 7 WOTs (including 4 

### 2022-09-29 2016-Weak-FH-Bisim/WeakBisim.tex
comments until p 23

@@
 and \emph{structural open automata} (finite) that can be generated as
-the semantics of pNets (see Definition \ref{def:operationalSemantics}), and used in the implementation. Then we define
+the semantics of pNets (see Definition \ref{def:operationalSemantics}), and used in their implementation. Then we define
 an alternative version of our bisimulation, called
@@
 FH-bisimulation, provided the logic of the predicates is
-decidable (proof can be found in \cite{henrio:Forte2016}). Formally:
+decidable (a proof of this claim can be found in \cite{henrio:Forte2016}). Formally:
 
@@
 $\mathcal{S}_2$ constrained by a set of predicates. Assume that
-the predicates inclusion is decidable over  
+the predicate inclusion is decidable over  
 the action algebra $\AlgA$. Then it is decidable whether the relation 
@@
 
-This section defines the semantics of an open pNet as a translation into an open automaton. 
-In this translation, the states of the open automata are obtained as products of 
+This section defines the semantics of an open pNet via translation into an open automaton. 
+In this translation, the states of the open automaton are obtained as products of 
 the states of the pLTSs at the leaves of the composition. The
@@
 bisimilarity relation for open pNets. As pNets are composition
-structures, it then makes sense to prove composition lemmas: we prove
+structures, it then makes sense to prove compositionality lemmas: we prove
 that the composition of strongly bisimilar pNets are themselves
@@
 To derive an open automaton from a pNet, we first describe the set of states of the automaton.
-Then we show the construction rule for transitions of the automaton, this  relies on the derivation of predicates unifying synchronisation vectors and the actions of the pNets involved in a given synchronisation.
+Then we show the construction rule for transitions of the automaton, which  relies on the derivation of predicates unifying synchronisation vectors and the actions of the pNets involved in a given synchronisation.
 
@@
 \begin{definition}[States of open pNets]\label{def-states}
-  A state of an open pNet is a tuple (not necessarily finite) of the
+  A state of an open pNet is a (not necessarily finite) tuple  of the
   states of its leaves.
@@
 \end{definition}
-To be precise, the state of each pLTS is entirely characterized by both the state of the automaton, and the value of its variables $V$.
-Consequently, the state of a pNet is not only characterized the tuple of pLTS states but also contains the value of its variables $\vars(P)$.
+To be precise, the state of each pLTS is entirely characterized by both the state of the automaton, and the values of its variables $V$. 
+%Consequently, the state of a pNet is not only characterized the tuple of pLTS states but also contains the value of its variables $\vars(P)$.
 
@@
 predicate $\Predsv$ is not satisfiable, then the transition associated with the 
-synchronisation will not occur in the considered state, or will occur with a \False\ precondition which is equivalent.
+synchronisation will not occur in the considered state, or equivalently will occur with a \False\ precondition.
 If the action families do not match or if there is no valuation of
@@
 
-\begin{definition}[Semantics of open pNets]
-	\label{def:operationalSemantics} The semantics of a pNet $\pNet$ is an open automaton $A\!= 
-	\mylangle \symb{Holes}(\pNet),\symb{States}(\pNet),\symb{InitState}(\pNet),\symb{vars}(P),\mathcal{T} \myrangle$ where $\mathcal{T}$   is the smallest set of open transitions such that $\mathcal{T}=\{OT\,|\,\pNet \models OT \}$ and	$\pNet \models OT$	is defined by the following  rules:
-%	\begin{itemize}
-%		\item $J$ is the set of holes: $Holes(p)= J$. 
-		%  \item $\set{L}^L = Leaves(p), \set{H}^J = Holes(p)$
-%		\item ${\mathcal{S}} = States(p)$ and $s_0 = InitState(p)$
-%		\item $\mathcal{T}$ is the smallest set of open transitions		satisfying the rules below:
-%	\end{itemize}
-
-	%% \TODO{ We should be careful here: after (re) reading "Huimin
-	%% 	Lin, 'Symbolic Transition Systems with Assignements', Concur'96" I
-	%% 	think handling assignments is not trivial, even for comparisons of pLTSs. }
-
-\begin{itemize}
-\item The rule for a pLTS  checks that the guard is verified and transforms assignments into post-conditions:		
+	\begin{figure}[tb]\label{fig:Tr1Tr2}
 \begin{mathpar}\inferrule
@@
 		}\quad {\TrUn}
-\end{mathpar}
-%	Note that this note is greatly simplified by the fact that variables are local to 
-%	thread; introducing global state variables or accepting loops to the same 
-%	state would 
-%	require to reason 
-%	on the scope of 
-%	each variables, and to introduce additional variables to handle the several occurence 
-%	of the same pLTS variable in the predicates. Indeed the constraints on pLTS 
-%	transitions 
-%	ensure that the same variable never appears both on the left and on the right of the 
-%	equations of a predicate.
-
-\item	The second rule deals with pNet nodes: for each possible
-	synchronisation vector (of index $k$) applicable to the rule subject, the premisses
-	include one {\em open transition} for each sub-pNet involved, one possible
-	{\em action} for each hole involved, and the predicate relating these
-	with the resulting action of the vector. The sub-pNets involved are split between two 
-	sets, $I_2$ for sub-pNets that are pLTSs (with open transitions obtained by rule \textbf{Tr1}), and $I_1$ for the sub-pNets that are not pLTSs (with open transitions obtained by rule \textbf{Tr2}), $J$ is the set of
-	holes involved in the transition\footnote{Formally, if $SV_k \!=\! \SV{({\alpha'})_m^{m 
-	\in M}}{\alpha'}{e_b}$ is a synchronisation vector  of \pNet\  then $J=M\cap 
-	\Holes(\pNet)$, $I_2=M\cap \Leaves(\pNet)$,  $I_1=M\setminus J \setminus 
-	I_2$}\footnote{We could replace $I_1$ and $I_2$ by their formal definition in \textbf{Tr2} but the rule would be more difficult to read.}.   
-\end{itemize}                                                                  
-\begin{mathpar}
+
+\\\\\\
+
     \mprset {vskip=.45ex}
@@
 \end{mathpar} 
-
-	\medskip
+\caption{Rules \TrUn\ and \TrDeux\ defining the semantics of  open pNets}
+\end{figure}
+
+\begin{definition}[Semantics of open pNets]
+	\label{def:operationalSemantics} The semantics of a pNet $\pNet$ is an open automaton $A\!= 
+	\mylangle \symb{Holes}(\pNet),\symb{States}(\pNet),\symb{InitState}(\pNet),\symb{vars}(P),\mathcal{T} \myrangle$ where $\mathcal{T}$   is the smallest set of open transitions such that $\mathcal{T}=\{OT\,|\,\pNet \models OT \}$ and	$\pNet \models OT$	is defined by the rules in Figure~\ref{fig:Tr1Tr2}
+%	\begin{itemize}
+%		\item $J$ is the set of holes: $Holes(p)= J$. 
+		%  \item $\set{L}^L = Leaves(p), \set{H}^J = Holes(p)$
+%		\item ${\mathcal{S}} = States(p)$ and $s_0 = InitState(p)$
+%		\item $\mathcal{T}$ is the smallest set of open transitions		satisfying the rules below:
+%	\end{itemize}
+
+	%% \TODO{ We should be careful here: after (re) reading "Huimin
+	%% 	Lin, 'Symbolic Transition Systems with Assignements', Concur'96" I
+	%% 	think handling assignments is not trivial, even for comparisons of pLTSs. }
+
+\begin{itemize}
+\item The rule \TrUn\ for a pLTS  checks that the guard is verified and transforms assignments into post-conditions.
+
+%\end{mathpar}
+%	Note that this note is greatly simplified by the fact that variables are local to 
+%	thread; introducing global state variables or accepting loops to the same 
+%	state would 
+%	require to reason 
+%	on the scope of 
+%	each variables, and to introduce additional variables to handle the several occurence 
+%	of the same pLTS variable in the predicates. Indeed the constraints on pLTS 
+%	transitions 
+%	ensure that the same variable never appears both on the left and on the right of the 
+%	equations of a predicate.
+
+\item	The  rule \TrDeux\ deals with pNet nodes: for each possible
+	synchronisation vector (of index $k$) applicable to the rule subject, the premisses
+	include one {\em open transition} for each sub-pNet involved, one possible
+	{\em action} for each hole involved, and the predicate relating these
+	with the resulting action of the vector. The sub-pNets involved are split between two 
+	sets, $I_2$ for sub-pNets that are pLTSs (with open transitions obtained by rule \textbf{Tr1}), and $I_1$ for the sub-pNets that are not pLTSs (with open transitions obtained by rule \TrDeux), $J$ is the set of
+	holes involved in the transition\footnote{Formally, if $SV_k \!=\! \SV{({\alpha'})_m^{m 
+	\in M}}{\alpha'}{e_b}$ is a synchronisation vector  of \pNet\  then $J=M\cap 
+	\Holes(\pNet)$, $I_2=M\cap \Leaves(\pNet)$,  $I_1=M\setminus J \setminus 
+	I_2$}\footnote{We could replace $I_1$ and $I_2$ by their formal definition in \TrDeux\ but the rule would be more difficult to read.}.   
+\end{itemize}                                                                  
+%\begin{mathpar}
+
 %        \TODO{may be explain how $\Pred(SV,a_i^{i\in I_k},b_j^{j\in
@@
 \end{definition}
-        	A key to understand this rule is that the open transitions are
+        	A key to understand \TrDeux\ is that the open transitions are
 	expressed in terms of the leaves and holes of the whole pNet structure,
-	i.e. a flatten view of the pNet. For example, $L$ is the index set of the
+	i.e. a flattened view of the pNet. For example, $L$ is the index set of the
 	Leaves, $L_m$ the index set of the leaves of one sub-pNet indexed $m$, so all $L_m$
@@
 holes, and each pLTS at leaves having a finite number of states and
-(symbolic) transitions, has a finite automaton. The algorithm for building such an automaton can be found in~\cite{QBMZ-AVOCS18}.
+(symbolic) transitions, induces a finite automaton. The algorithm for building such an automaton can be found in~\cite{QBMZ-AVOCS18}.
 
@@
 \end{thm}
-This theorem is quite powerful.
-It somehow implies that the theory of open pNets is convenient to study properties of process composition.
-Open pNets can indeed be used to study process operators and process algebras, as shown in~\cite{henrio:Forte2016} where compositional properties are extremely useful.
-In the case of interaction protocols~\cite{BHHM:FACS11}, composition of bisimulation can justify abstractions used in some parts of the application.
+This theorem is quite powerful, as it somehow implies that the theory of open pNets can be used to study properties of process composition.
+Open pNets can indeed be applied to study process operators and process algebras, as shown in~\cite{henrio:Forte2016} where compositional properties are extremely useful.
+In the case of interaction protocols~\cite{BHHM:FACS11}, compositionality of bisimulation can justify abstractions used in some parts of the application.
 
@@
 The notion of non-observable actions varies in different contexts,
-e.g. $tau$ in CCS \cite{Milner:1982,Milner:1989}, and $i$ in Lotos \cite{BOLOGNESI:1987}, we could define classically a set of
+e.g. $tau$ in CCS \cite{Milner:1982,Milner:1989}, and $i$ in Lotos \cite{BOLOGNESI:1987}. We could define classically a set of
 \emph{internal/non-observable actions} depending on a specific action

### 2022-10-04 2016-Weak-FH-Bisim/WeakBisim.tex
and rules

@@
 including notions of symbolic behavioural semantics and various symbolic 
-bisimulations (early and late, strong and weak, and their congruent versions). They also extended this work to models with explicit assignments \cite{Linconcur96}.
+bisimulations (early and late, strong and weak, and their congruent versions). They also extended this work to models with explicit assignments \cite{Lin:96}.
 Separately Rathke~\cite{HennessyRathke:TCS98} defined another symbolic semantics for 
@@
 	\begin{figure}[tb]\label{fig:Tr1Tr2}
-\begin{mathpar}\inferrule
+\[\inferrule
 		{ s \xrightarrow{\langle \alpha,~e_b,~(x_j\!:= {e}_j)^{j\in
@@
 		}\quad {\TrUn}
-
-\\\\\\
-
+\]
+~\qquad and
+\[
     \mprset {vskip=.45ex}
@@
     }\quad {\TrDeux}
-\end{mathpar} 
+\]
 \caption{Rules \TrUn\ and \TrDeux\ defining the semantics of  open pNets}
@@
 
-Weak symbolic bisimulation \cite{HENNESSY:1995} was introduced to relate transition systems
+Weak symbolic bisimulation \cite{HennessyLin:TCS95} was introduced to relate transition systems
 that have indistinguishable behaviour, with respect to some definition
@@
  As mentioned in the \emph{Introduction}, the work that brought us a lot of inspirations are those of Lin et al.
-\cite{IngolfsdottirL:2001,HennessyLin:TCS95,Linconcur96}.
+\cite{IngolfsdottirL:2001,HennessyLin:TCS95,Lin:96}.
 They developed the theory of symbolic transition graphs (STG), and the associated symbolic (early and late, strong and weak) bisimulations, they also study STGs with assignments as a model for message-passing processes.
@@
 symbolic semantics in term of open automata \cite{QBMZ-AVOCS18}, and have
-developed algorithms to check strong FH-bisimulation and weak FH-bisimulation \cite{hou:hal-02406098,PEPS}.
+developed algorithms to check strong FH-bisimulation and weak FH-bisimulation \cite{hou:hal-02406098,WangMZ:2021}.
 The challenges here, in the context of our symbolic systems, is not so much algorithmic complexity,
@@
 
-\bibliographystyle{alpha}
+\bibliographystyle{plain}
 

### 2022-10-04 2016-Weak-FH-Bisim/WeakBisim.tex
references

@@
 Consider a pNet node that assembles several pLTSs, the synchronisation vectors specify the way that transitions of the composed pNet are built from the transitions of the sub-nets.
-This can be seen as ``conditional transitions'' of the pNet, or alternatively, as a syntax to encode structural operational semantics (SOS rules) \cite{deSimone85} of the system: each vector expresses not only the actions emitted by the pNet but also what transitions of the composed pLTSs must occur to trigger this global transition.
+This can be seen as ``conditional transitions'' of the pNet, or alternatively, as a syntax to encode structural operational semantics (SOS rules) \cite{plotkin:2004} of the system: each vector expresses not only the actions emitted by the pNet but also what transitions of the composed pLTSs must occur to trigger this global transition.
 Synchronisation vectors can also express the exportation of an action of a sub-pNet to the next level, or to hide an interaction and make it non-observable.
@@
 \begin{figure}[t]
-   \includegraphics[width=.37\textwidth]{XFIG/SimpleProt-Schema.pdf}
+   \includegraphics[width=.37\textwidth]{XFIG/SimpleProt-Schema1.pdf}
    \includegraphics[width=.62\textwidth]{XFIG/SimpleProt2-Spec.pdf}

### 2022-10-04 2016-Weak-FH-Bisim/WeakBisim.tex
more typos

--- 2022-10-04 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 \emph{internal/non-observable actions} depending on a specific action
-algebra. In this paper, to simplify the notations, we will simply use $\tau$ as the single non-observable action; the generalisation of our results to a set of non-observable actions is trivial. 
+algebra.
+However in this paper, to simplify the notations, we will simply use $\tau$ as the single non-observable action; the generalisation of our results to a set of non-observable actions is trivial.
 Naturally, a non-observable action cannot be synchronised with
@@
 This allows us to define weak open automata, and a weak bisimulation relation based on these weak open automata.
-Finally, we apply this weak bisimulation to open pNets, obtain a weak bisimilarity relationship for open pNets, and prove that this relation has compositional properties.
+Finally, we apply this weak bisimulation to open pNets, obtain a weak bisimilarity relation for open pNets, and prove that this relation has compositional properties.
 
@@
 We first specify in terms of open transition, what it means for an action to be non-observable.
-Namely, we constraint ourselves to system where the emission of a $\tau$ action by a sub-pNet cannot be observed by the surrounding pNets.
-In other words, a pNet cannot change its state, or emit a specific observable action when one of its holes emits a $\tau$ action.
+We first define (in Definition~\ref{def:Non-ObsTau}) systems that cannot observe $\tau$ actions of sub-systems; namely pNets that cannot change their state, or emit an observable action when one of its holes emits a $\tau$ action.
 
@@
 Because of the non-observability property (Definition~\ref{def:Non-ObsTau}), it is possible to add any number of $\tau$ transitions of the holes before or after any open transition freely.
-This property justifies the fact that we can abstract away $\tau$ transitions from holes in the definition of a weak open transition.
+This property justifies the fact that we can abstract away from $\tau$ transitions from holes in the definition of a weak open transition.
 We define weak open transitions similarly to open transitions except that holes can perform \emph{sequences of observable actions} instead of single actions (observable or not).
@@
 We are now able to build a weak open automaton from an open automaton.
-This is done in a way that resembles the process of $\tau$ saturation: we add  $\tau$ open transitions before or after another (observable or not) open transition.
+This is done in a way that resembles the process of $\tau$ saturation: we add  $\tau$ open transitions before or after another open transition, regardless of whether it is observable or not.
 \begin{definition}[Building a weak open automaton]\label{def:buildweakOT}~\\
   Let $A = \mylangle J,\mathcal{S},s_0,V,\mathcal{T}\myrangle$ be an open automaton. 
-The weak open automaton \emph{derived} from $A$ is an open automaton  $\mylangle J,\mathcal{S},s_0,V,\WT\myrangle$ where $\WT$ is derived from $\mathcal{T}$ by saturation, applying the following rules:
+The weak open automaton \emph{derived} from $A$ is an open automaton  $\mylangle J,\mathcal{S},s_0,V,\WT\myrangle$ where $\WT$ is derived from $\mathcal{T}$ by saturation, applying the rules of Figure~\ref{fig:WT}:
 %\noindent{\bf Invisible $\tau$ transitions:}
-\begin{mathpar}
- \openrule
+\begin{figure}[tb]
+\begin{mathpar}
+ {\openrule
          {
            \emptyset,\symb{True},\Id(V)}
-         {s \OTWeakarrow {\tau} s} \in \WT  \qquad \WTUn
- \end{mathpar}
-and
-\begin{mathpar}
+         {s \OTWeakarrow {\tau} s} \in \WT  \quad \WTUn}
+\qquad\quad
+\text{and}
+%\noindent{\bf Other transitions:}
+\qquad\quad
 \inferrule{
@@
 \end{mathpar}
-
+\caption{Weak transition definition}\label{fig:WT}
+\end{figure}
 \end{definition}
-Rule $\WTUn$ states that it is always possible to do a non-observable transition, where the state is unchanged and the holes perform no action.
-Rule~$\WTDeux$ states that each open transition can be considered as a weak open transition.
-The last rule is the most interesting:  Rule~$\WTTrois$ allows any number of $\tau$ transitions before or after any weak open transition.
-This rules carefully composes predicates, effects, and actions of the holes, indeed in the rule, predicate $\Pred_2$ manipulates variables of $s_1$ that result from the first weak open transition.
+Rule $\WTUn$ states that it is always possible to perform a non-observable transition, where the state is unchanged and the holes perform no action.
+Rule~$\WTDeux$ states that each open transition is a weak open transition.
+Finally,  Rule~$\WTTrois$ allows any number of $\tau$ transitions before or after any weak open transition.
+This rule carefully composes predicates, effects, and actions of the holes.
+Indeed, predicate $\Pred_2$ manipulates variables of $s_1$ that result from the first weak open transition.
 Their values thus depend on the initial state but also on the effect (as a substitution function $\Post_1$) of the first weak open transition.
 In the same manner, $\Pred_3$ must be applied the substitution defined by the composition $\Post_2\shortodot\Post_1$.
-Similarly, effects on variables must be applied to obtain the global effect of the composed weak open transition, it must also be applied to observable actions of the holes, and to the global action of the weak open transition.
+Similarly, effects on variables must be applied to obtain the global effect of the composed weak open transition, to observable actions of the holes, and to the global action of the weak open transition.
 

### 2022-10-05 2016-Weak-FH-Bisim/WeakBisim.tex
visio result

@@
 equivalences, and developed a symbolic model-checker based on a tableau
-method for these processes. Thirty years later, no
-practical verification method and no verification platform use this kind of approaches to provide proof methods for value-passing processes or open process expressions.
+method for these processes.
+Thirty years later,  no verification platform use this kind of approaches to provide proof methods for value-passing processes or open process expressions, perhaps because of the difficulty to apply these methods on industrial systems.
 
@@
 Two open automata are FH-bisimilar if there exists an FH-bisimulation that relates their initial states\footnote{I.e., the predicate relation associated to the initial states is \True.}.
+We call this relation \emph{FH-bisimilarity}.
 

### 2022-10-05 2016-Weak-FH-Bisim/WeakBisim.tex
marque les TODO de ce matin

@@
 The semantics of pNets can be expressed as a translation to a labelled transition system (LTS), but only if the pNet has no parameter and no hole.
-Adding parameters to a LTS is quite standard but enabling holes inside LTSs is not a standard notion.
+Adding parameters to a LTS is quite standard \ERIC{\cite{Lin:96}} but enabling holes inside LTSs is not a standard notion.
 
@@
 Instead, bisimulation for open automata  relies on the simulation of each open transition of one automaton by \emph{a set of} open transitions of the other one, that should cover all the
-cases where the original transition can be triggered.
+cases where the original transition can be triggered. \TODO{Eric: is this like in symbolic bisimulation ?}
 
 Compositionality of bisimilarity in our model comes from the specification of the interactions, including actions of the holes. 
+\ERIC{This is quite different from the works on contextual equivalences, e.g. \cite{sec:RW}; we will give more details on this in section \ref{}.}
 In pNets, synchronisation vectors define the possible interactions between the pNet that fills the hole and the surrounding pNets.
@@
 This approach also allows us to specify a sufficient condition on allowed transitions to make weak bisimilarity compositional; namely it is not possible to synchronise on invisible actions from the holes or prevent them to occur.
+\TODO{Eric: relations with SOS rule formats?}
 
@@
 $t\in\AlgT$.
+\TODO{Ludo: footnote or remark on Sorts/types/vars/signatures}
 
@@
 the actions it exposes.
+\TODO{Rabea: look for papers by Larsen end Liu on context systems, and Larsen and Huttel on static constructs}
 
@@
 
+\TODO{Ludo: a sentence on inspiration from RdS, and forward link to related work}
+
 The semantics of open pNets will be defined  as an open automaton. An open
@@
  that pioneered this idea.
+\TODO{Eric: combination of RdS, symb bisim, and more}
 
@@
 The definition of this predicate is not constructive but it is easy to build the predicate constructively by brute-force unification of the sub-pNets actions with the corresponding vector actions, possibly followed by a simplification step.
+\TODO{Eric: replace by what we do in the tool, plus cite\{avocs\} }
 
@@
 We first define (in Definition~\ref{def:Non-ObsTau}) systems that cannot observe $\tau$ actions of sub-systems; namely pNets that cannot change their state, or emit an observable action when one of its holes emits a $\tau$ action.
+\TODO{Eric: discuss rel with Vaandrager}
 
@@
 These works clearly highlight the interest of incremental and compositional verification in a very general setting.
-In our own work on open pNets, adding more structure to the composition model, we show how to enforce a compositional proof system that is more powerful than independent sets of variables.
+In our own work on open pNets, adding more structure to the composition model, we show how to enforce a compositional proof system that is more powerful than independent sets of variables\TODO{Ludo}.
 Our theory has also been encoded into an SMT solver and it would be interesting to investigate how the examples of evolving systems studied by the authors could be encoded into pNet and verified by our framework.
@@
 Defining properly the interaction between a logical formulae in the action and the logics of the pNet composition seems very difficult.
+\TODO{Rabea: look for "quotienting techniques"}
 
@@
  Feng et al. provide a symbolic bisimulation for quantum processes \cite{feng2014symbolic}.
-All the above works, did not give a complete approach for verification, and the models on which these works based are definitely different from ours.
+All the above works, did not give a complete approach for verification \TODO{Ludo}, and the models on which these works based are definitely different from ours.
 
@@
 VCE is the specification and verification platform that uses pNets as an intermediate representation.
+\TODO{Eric: short mentions and links to our tools and examples papers}
 
@@
 defined here a semantics for open pNets and a complete bisimulation theory for them. 
-The semantics of open pNets relies on the definition of open automata that are automata with holes and parameters, but no hierarchy.
+The semantics of open pNets relies on the definition of open automata that are automata with holes and parameters, but no hierarchy \TODO{Ludo: flatten}.
 Open automata are somehow labelled transition systems with parameters and holes, a notion that is useful to define semantics, but makes less sense when modelling a system, compared to pNets.
@@
 Our strong  FH-bisimilarity is compositional by nature in the sense that FH-bisimilarity is maintained when composing processes.
-We also identified a simple and realistic condition on the semantics of non-observable actions that allows weak FH-bisimilarity to be also compositional.
+We also identified a simple and realistic condition on the semantics of non-observable actions that allows weak FH-bisimilarity to be also compositional \TODO{Eric: recall on rule formats}.
 Overall we believe that this article paved the way for a solid theoretical foundation for compositional verification of parallel and distributed systems.

### 2022-10-05 2016-Weak-FH-Bisim/WeakBisim.tex
typos until RW

--- 2022-10-05 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 These are however technically more complex than the ones for open automata because each hole performs a set of actions, and thus a composed transition is the composition of one transition of the top-level pNet and a sequence of transitions of the sub-pNet that fills its hole.
-They can be found as Lemmas~\ref{lem-decomposeWOT}, Lemma~\ref{lem-Weakcompose1}, and Lemma~\ref{lem-Weakcompose} in~\ref{sec:app-composition}.
+Composition and decomposition properties can be found as Lemmas~\ref{lem-decomposeWOT}, Lemma~\ref{lem-Weakcompose1}, and Lemma~\ref{lem-Weakcompose} in~\ref{sec:app-composition}.
 
@@
 For defining a bisimulation relation between weak open automata, two options are possible.
-Either we define a simulation similar to the strong simulation but based on open automata, this would look like the FH-simulation but would need to be adapted to weak open transitions.
-Or we define directly and classically a weak FH-simulation as a relation between two open automata, relating the open transition of the first one with the transition of the weak open automaton derived from the second one.
+One option is that we define a simulation similar to the strong simulation but based on open automata, this would look like the FH-simulation but would need to be adapted to weak open transitions.
+Alternatively, we could define directly and classically a weak FH-simulation as a relation between two open automata, relating the open transitions of the first one with the transitions of the weak open automaton derived from the second one.
 
 The definition below specifies how a set of weak open transitions can simulate an open transition, and under which condition; this is used to relate, by weak FH-bisimulation, two open automata by reasoning on the weak open automata that can be derived from the strong ones.
-This is defined formally as follows.
 
@@
 
-Two open automata are weak FH-bisimilar if there exists a weak FH-bisimulation relation that relates their initial states.
+Two open automata are \emph{weak FH-bisimilar} if there exists a weak FH-bisimulation relation that relates their initial states. This relation is called \emph{weak FH-bisimilarity}.
 Two pNets are weak FH-bisimilar if their associated open automata are weakly bisimilar.
@@
 
-Our first important result is that weak FH-bisimilarity is an equivalence in the same way as strong FH-bisimilarity:
+Our first important result is that weak FH-bisimilarity is an equivalence in the same way as strong FH-bisimilarity.
 
@@
 \cite{Johnson:2013:CBSE,Johnson:2014:qosa}, the authors investigate several methodologies for the compositional verification of software systems, with the aim to verify reconfigurable component systems.
-To improve scaling and compositionality, the authors  decouple the verification problem that is to be resolved by a SMT (satisfiability modulo theory) solver into independent sub-problems on independent sets of variables.
+To improve scaling and compositionality, the authors  decompose the verification problem that is to be resolved by a SMT (satisfiability modulo theory) solver into independent sub-problems on independent sets of variables.
 These works clearly highlight the interest of incremental and compositional verification in a very general setting.
-In our own work on open pNets, adding more structure to the composition model, we show how to enforce a compositional proof system that is more powerful than independent sets of variables.
-Our theory has also been encoded into an SMT solver and it would be interesting to investigate how the examples of evolving systems studied by the authors could be encoded into pNet and verified by our framework.
+In our own work on open pNets, adding more structure to the composition model, we show how to enforce a compositional proof system that is more versatile than independent sets of variables as the composition is  structured and allows arbitrary synchronisations between sub-entities.
+Our theory has also been encoded into an SMT solver and it would be interesting to investigate how the examples of evolving systems studied by Johnson et al.
+could be encoded into pNet and verified by our framework.
 However, the models of Johnson et al.
@@
 on some kinds of labelled transition systems.
-The distinguishing feature of their approach is the transitions systems are labelled with logical formulae that provides  an abstract characterization of the structure that a hole must possess and of the actions it can perform in order to allow a transition to fire.
+The distinguishing feature of their approach is that the transitions systems are labelled with logical formulae that provides  an abstract characterization of the structure that a hole must possess and of the actions it can perform in order to allow a transition to fire.
 Logical formulae are suitable formats that capture the general class of components that can act as the placeholders of the system during its evolution.

### 2022-10-05 2016-Weak-FH-Bisim/WeakBisim.tex
comments up to conclusion

@@
 are quite different from ours, in particular they are much less structured, and translating them is clearly outside the scope of this article.
+
 In previous work~\cite{GasparHM:2013}, we also have shown how (closed) pNet models could be used to encode and verify finite instances of reconfigurable component systems. 
@@
 The distinguishing feature of their approach is that the transitions systems are labelled with logical formulae that provides  an abstract characterization of the structure that a hole must possess and of the actions it can perform in order to allow a transition to fire.
-Logical formulae are suitable formats that capture the general class of components that can act as the placeholders of the system during its evolution.
+Logical formulae are suitable formalisms that capture the general class of components that can act as the placeholders of the system during its evolution.
 In our approach we purposely leave the algebra of action terms undefined but the only operation we allow on action of holes is the comparison with other actions.
 Defining properly the interaction between a logical formulae in the action and the logics of the pNet composition seems very difficult.
+\TODO{Rabea: look for "quotienting techniques"}
 
@@
 The approach of  \cite{Beohar:2020} is
-  highly based on logics and their bisimulation theory richer in this aspect, while our theory is highly structural and focuses on relation between structure and equivalence.
-Also, we see composition as a structural operation putting systems together, and do not focus on the modelisation of an unknown outside world.
-Overall we believe that the two approaches are complementary but checking the compatibility of the two different bisimulation theories is not  trivial.
+  highly based on logics and their bisimulation theory is richer than ours in this aspect, while our theory is highly structural and focuses on relation between structure and equivalence.
+Also, we see composition as a structural operation putting systems together, and do not focus on the modelling of an unknown outside world.
+Overall we believe that the two approaches are complementary but comparing precisely the two different bisimulation theories is not  trivial.
 
@@
 A formal comparison would be interesting, though not trivial.
-What we can say easily is that: the pNet format syntactically encompasses both DeSimone, GSOS, and conditional premisses rules.
+What we can say easily is that: the pNet format syntactically encompasses  De Simone, GSOS, and conditional premisses rules.
 Then our compositionality result is more powerful than their classical results, but this is not a surprise, as we rely on a (sufficient) syntactic hypothesis on a particular system, rather than the general rules defining an operator.
 Last, we intentionally do not accept negative premisses, that would be more  to put into practice in our implementation.
-an extension could be studied in future work.
+This extension could be studied in future work.
 
 \subsubsection*{Symbolic and data-sensitive systems}
- As mentioned in the \emph{Introduction}, the work that brought us a lot of inspirations are those of Lin et al.
+ As mentioned in the \emph{Introduction}, we were substantially inspired by the works  of Lin et al.
 \cite{IngolfsdottirL:2001,HennessyLin:TCS95,Lin:96}.
-They developed the theory of symbolic transition graphs (STG), and the associated symbolic (early and late, strong and weak) bisimulations, they also study STGs with assignments as a model for message-passing processes.
-Our work extends these in several ways: first our models are compositional, and our bisimulations come with effective conditions for being preserved by pNet composition (i.e.
+They developed the theory of symbolic transition graphs (STG), and the associated symbolic (early and late, strong and weak) bisimulations.
+Moreover, they studied STGs with assignments as a model for message-passing processes.
+Our work extends those contributions in several ways: first our models are compositional, and our bisimulations come with effective conditions for being preserved by pNet composition (i.e.
 congruent), even for the weak version.
@@
 and Buscemi et al.
-providing symbolic semantic and equivalence for different variants of pi calculus respectively \cite{BorgstromBN04,DelauneKR:2007,LiuL:2010,BuscemiM:2008}; and more recently
+providing symbolic semantics and equivalence for different variants of pi calculus respectively \cite{BorgstromBN04,DelauneKR:2007,LiuL:2010,BuscemiM:2008}; and more recently
  Feng et al. provide a symbolic bisimulation for quantum processes \cite{feng2014symbolic}.
-All the above works, did not give a complete approach for verification, and the models on which these works based are definitely different from ours.
+\TODO{check next sentence}
+All the above works are based on models  definitely different from ours, and none of them allows system to be as much parameterised as open pNets; this additional expressiveness due to the open and symbolic nature of our constructs.
 
@@
 \label{section:conclusion}
- pNets (Parameterised Networks of Automata) is a formalism adapted to the representation of the behaviour of a parallel or distributed systems.
-One  strength of pNets is their parameterised nature, making them adapted to the representation of systems of arbitrary size, and making the modelling of parameterised system possible.
+ pNets (Parameterised Networks of Automata) is a formalism adapted to the representation of the behaviour of  parallel or distributed systems.
+One  strength of pNets is their parameterised nature, making them suitable for to the representation of systems of arbitrary size, and making the modelling of parameterised system possible.
 Parameters are also crucial to reason on interaction protocols that can address one entity inside an indexed set of processes.

### 2022-10-05 2016-Weak-FH-Bisim/WeakBisim.tex
comments

@@
  pNets (Parameterised Networks of Automata) is a formalism adapted to the representation of the behaviour of  parallel or distributed systems.
-One  strength of pNets is their parameterised nature, making them suitable for to the representation of systems of arbitrary size, and making the modelling of parameterised system possible.
-Parameters are also crucial to reason on interaction protocols that can address one entity inside an indexed set of processes.
+One  strength of pNets is their parameterised nature, making them suitable for to the representation of systems of arbitrary size, and making the modelling of parameterised systems possible.
+Parameters are also crucial to reason about interaction protocols that can address one entity inside an indexed set of processes.
 pNets have been successfully used to represent behavioural specification of parallel and distributed components and verify their correctness~\cite{AmeurBoulifa2017,HenrioKSM:2016}.
@@
 Open pNets are pNets with holes; they are adapted to represent processes parameterised by the behaviour of other processes, like composition operators or interaction 
-protocols that synchronise the actions of processes that can be plugged afterwards. Open
+protocols that synchronise the actions of processes that can be provided afterwards. Open
 pNets are hierarchical composition of automata with holes and parameters. We
 defined here a semantics for open pNets and a complete bisimulation theory for them. 
-The semantics of open pNets relies on the definition of open automata that are automata with holes and parameters, but no hierarchy \TODO{Ludo: flatten}.
-Open automata are somehow labelled transition systems with parameters and holes, a notion that is useful to define semantics, but makes less sense when modelling a system, compared to pNets.
+The semantics of open pNets relies on the definition of open automata that are automata with holes and parameters, but no hierarchy.
+\TODO{check this sentence} Open atomata are a flattened view of the pNet; their behaviour is expressed as open transitions that allow for a more semantic interpretation of parameters than pNets.
+Open automata are  labelled transition systems with parameters and holes, a notion that is useful to define semantics, but makes less sense when modelling a system, compared to pNets.
 To be precise, it is on open automata that we define our FH-bisimilarity relations.
@@
 Our FH-bisimulation principle handles pNet parameters in the sense that two states might be or not in relation depending on the value of parameters.
-Our strong  FH-bisimilarity is compositional by nature in the sense that FH-bisimilarity is maintained when composing processes.
+Our strong  FH-bisimilarity is compositional  in the sense that FH-bisimilarity is maintained when composing processes.
 We also identified a simple and realistic condition on the semantics of non-observable actions that allows weak FH-bisimilarity to be also compositional \TODO{Eric: recall on rule formats}.
@@
 
-pNets support the refinement checking at the automata level through a simulation approach, with symbolic evaluation of
+pNets support the refinement checking at the automaton level through a simulation approach, with symbolic evaluation of
 the guards and transitions. 
  The definition of simulation on open automata should be  stronger than a strict simulation since it matches a transition with a family of transitions.
-Such a relation should be able to check the refinement between two open automata with the same level of abstraction but specified differently, for example, by duplicating states, removing transitions, reinforcing guards, modifying variables.
+Such a relation should be able to check the refinement between two open automata with the same level of abstraction but specified differently, for example, by duplicating states, removing transitions, strengthening guards, modifying variables.
 Additionally, composition of
@@
 the relations with existing equivalences on both closed and open systems. In particular, our model being significantly different from those considered in \cite{IngolfsdottirL:2001}, it
-would be interesting to compare our ``FH'' family of bisimulations with the hierarchy of symbolic bisimulations from these authors.
+would be interesting to compare our ``FH'' family of bisimulations with the hierarchy of symbolic bisimulations from those authors.
 We also plan to apply open pNets to the study of complex composition
@@
 developed algorithms to check strong FH-bisimulation and weak FH-bisimulation \cite{hou:hal-02406098,WangMZ:2021}.
-The challenges here, in the context of our symbolic systems, is not so much algorithmic complexity,
+The challenges here, in the context of our symbolic systems, are not so much algorithmic complexity,
 as was the case with classical weak bisimulation on finite models, but decidability and termination.
@@
 so we prefer a direct implementation of the weak bisimulation definition, without
-constructing the weak automata, but searching \emph{on demand} to construct the required weak transitions.
+constructing the weak automata beforehand, but searching \emph{on demand} to construct the required weak transitions.
 Beside, we explore in \cite{wang:hal-03126313} more pragmatic approaches using weak bisimulation preserving (pattern-based) 
@@
 
-We introduce the following predicate (we will need it for reasoning on the global predicate and will reason on it along the proof):\\
+We introduce the following predicate (we will need it for reasoning about the global predicate and will reason about it along the proof):\\
 $\begin{array}{l}\displaystyle{

### 2022-10-05 2016-Weak-FH-Bisim/WeakBisim.tex
footnote variables

@@
 \AlgE\cap\AlgA=\emptyset$;
-naturally action terms will use data expressions as sub-terms.
+naturally action terms will use data expressions as sub-terms\footnote{In our tools, we use datatypes for the different kinds of terms.
+In this article, we use different sets of variables for variables and terms of different kinds.}.
 The function $\vars(t)$ identifies the set of variables in a term
 $t\in\AlgT$.
-\TODO{Ludo: footnote or remark on Sorts/types/vars/signatures}
+\TODO{check footnote}
 

### 2022-10-06 2016-Weak-FH-Bisim/WeakBisim.tex
done pages 18 and 36

--- 2022-10-05 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 Compositionality of bisimilarity in our model comes from the specification of the interactions, including actions of the holes. 
-\ERIC{This is quite different from the works on contextual equivalences, e.g. \cite{sec:RW}; we will give more details on this in section \ref{}.}
+\ERIC{This is quite different from the works on contextual equivalences, e.g. \cite{Larsen}; we will give more details on this in section \ref{sec:RW}.}
 In pNets, synchronisation vectors define the possible interactions between the pNet that fills the hole and the surrounding pNets.
@@
 
-The definition of this predicate is not constructive but it is easy to build the predicate constructively by brute-force unification of the sub-pNets actions with the corresponding vector actions, possibly followed by a simplification step.
+% but it is easy to build the predicate constructively by brute-force unification of the sub-pNets actions with the corresponding vector actions, possibly followed by a simplification step.
 \TODO{Eric: replace by what we do in the tool, plus cite\{avocs\} }
+The definition of this predicate is not constructive. In our tool \cite{qin:hal-01823507}, we construct a logical formula encoding the matching 
+and unification condition involved, and we let an SMT engine (in the current implementation Z3) decide its satisfiability.
 
@@
 These are however technically more complex than the ones for open automata because each hole performs a set of actions, and thus a composed transition is the composition of one transition of the top-level pNet and a sequence of transitions of the sub-pNet that fills its hole.
-Composition and decomposition properties can be found as Lemmas~\ref{lem-decomposeWOT}, Lemma~\ref{lem-Weakcompose1}, and Lemma~\ref{lem-Weakcompose} in~\ref{sec:app-composition}.
+They can be found as Lemmas~\ref{lem-decomposeWOT}, Lemma~\ref{lem-Weakcompose1}, and Lemma~\ref{lem-Weakcompose} in~\ref{sec:app-composition}.
 
@@
 For defining a bisimulation relation between weak open automata, two options are possible.
-One option is that we define a simulation similar to the strong simulation but based on open automata, this would look like the FH-simulation but would need to be adapted to weak open transitions.
-Alternatively, we could define directly and classically a weak FH-simulation as a relation between two open automata, relating the open transitions of the first one with the transitions of the weak open automaton derived from the second one.
+Either we define a simulation similar to the strong simulation but based on open automata, this would look like the FH-simulation but would need to be adapted to weak open transitions.
+Or we define directly and classically a weak FH-simulation as a relation between two open automata, relating the open transition of the first one with the transition of the weak open automaton derived from the second one.
 
 The definition below specifies how a set of weak open transitions can simulate an open transition, and under which condition; this is used to relate, by weak FH-bisimulation, two open automata by reasoning on the weak open automata that can be derived from the strong ones.
+This is defined formally as follows.
 
@@
 
-Two open automata are \emph{weak FH-bisimilar} if there exists a weak FH-bisimulation relation that relates their initial states. This relation is called \emph{weak FH-bisimilarity}.
+Two open automata are weak FH-bisimilar if there exists a weak FH-bisimulation relation that relates their initial states.
 Two pNets are weak FH-bisimilar if their associated open automata are weakly bisimilar.
@@
 
-Our first important result is that weak FH-bisimilarity is an equivalence in the same way as strong FH-bisimilarity.
+Our first important result is that weak FH-bisimilarity is an equivalence in the same way as strong FH-bisimilarity:
 
@@
 \cite{Johnson:2013:CBSE,Johnson:2014:qosa}, the authors investigate several methodologies for the compositional verification of software systems, with the aim to verify reconfigurable component systems.
-To improve scaling and compositionality, the authors  decompose the verification problem that is to be resolved by a SMT (satisfiability modulo theory) solver into independent sub-problems on independent sets of variables.
+To improve scaling and compositionality, the authors  decouple the verification problem that is to be resolved by a SMT (satisfiability modulo theory) solver into independent sub-problems on independent sets of variables.
 These works clearly highlight the interest of incremental and compositional verification in a very general setting.
-In our own work on open pNets, adding more structure to the composition model, we show how to enforce a compositional proof system that is more versatile than independent sets of variables as the composition is  structured and allows arbitrary synchronisations between sub-entities.
-Our theory has also been encoded into an SMT solver and it would be interesting to investigate how the examples of evolving systems studied by Johnson et al.
-could be encoded into pNet and verified by our framework.
+In our own work on open pNets, adding more structure to the composition model, we show how to enforce a compositional proof system that is more powerful than independent sets of variables\TODO{Ludo}.
+Our theory has also been encoded into an SMT solver and it would be interesting to investigate how the examples of evolving systems studied by the authors could be encoded into pNet and verified by our framework.
 However, the models of Johnson et al.
 are quite different from ours, in particular they are much less structured, and translating them is clearly outside the scope of this article.
-
 In previous work~\cite{GasparHM:2013}, we also have shown how (closed) pNet models could be used to encode and verify finite instances of reconfigurable component systems. 
@@
 on some kinds of labelled transition systems.
-The distinguishing feature of their approach is that the transitions systems are labelled with logical formulae that provides  an abstract characterization of the structure that a hole must possess and of the actions it can perform in order to allow a transition to fire.
-Logical formulae are suitable formalisms that capture the general class of components that can act as the placeholders of the system during its evolution.
+The distinguishing feature of their approach is the transitions systems are labelled with logical formulae that provides  an abstract characterization of the structure that a hole must possess and of the actions it can perform in order to allow a transition to fire.
+Logical formulae are suitable formats that capture the general class of components that can act as the placeholders of the system during its evolution.
 In our approach we purposely leave the algebra of action terms undefined but the only operation we allow on action of holes is the comparison with other actions.
@@
 The approach of  \cite{Beohar:2020} is
-  highly based on logics and their bisimulation theory is richer than ours in this aspect, while our theory is highly structural and focuses on relation between structure and equivalence.
-Also, we see composition as a structural operation putting systems together, and do not focus on the modelling of an unknown outside world.
-Overall we believe that the two approaches are complementary but comparing precisely the two different bisimulation theories is not  trivial.
+  highly based on logics and their bisimulation theory richer in this aspect, while our theory is highly structural and focuses on relation between structure and equivalence.
+Also, we see composition as a structural operation putting systems together, and do not focus on the modelisation of an unknown outside world.
+Overall we believe that the two approaches are complementary but checking the compatibility of the two different bisimulation theories is not  trivial.
 
@@
 A formal comparison would be interesting, though not trivial.
-What we can say easily is that: the pNet format syntactically encompasses  De Simone, GSOS, and conditional premisses rules.
+What we can say easily is that: the pNet format syntactically encompasses both DeSimone, GSOS, and conditional premisses rules.
 Then our compositionality result is more powerful than their classical results, but this is not a surprise, as we rely on a (sufficient) syntactic hypothesis on a particular system, rather than the general rules defining an operator.
 Last, we intentionally do not accept negative premisses, that would be more  to put into practice in our implementation.
-This extension could be studied in future work.
+an extension could be studied in future work.
 
 \subsubsection*{Symbolic and data-sensitive systems}
- As mentioned in the \emph{Introduction}, we were substantially inspired by the works  of Lin et al.
+ As mentioned in the \emph{Introduction}, the work that brought us a lot of inspirations are those of Lin et al.
 \cite{IngolfsdottirL:2001,HennessyLin:TCS95,Lin:96}.
-They developed the theory of symbolic transition graphs (STG), and the associated symbolic (early and late, strong and weak) bisimulations.
-Moreover, they studied STGs with assignments as a model for message-passing processes.
-Our work extends those contributions in several ways: first our models are compositional, and our bisimulations come with effective conditions for being preserved by pNet composition (i.e.
+They developed the theory of symbolic transition graphs (STG), and the associated symbolic (early and late, strong and weak) bisimulations, they also study STGs with assignments as a model for message-passing processes.
+Our work extends these in several ways: first our models are compositional, and our bisimulations come with effective conditions for being preserved by pNet composition (i.e.
 congruent), even for the weak version.
@@
 and Buscemi et al.
-providing symbolic semantics and equivalence for different variants of pi calculus respectively \cite{BorgstromBN04,DelauneKR:2007,LiuL:2010,BuscemiM:2008}; and more recently
+providing symbolic semantic and equivalence for different variants of pi calculus respectively \cite{BorgstromBN04,DelauneKR:2007,LiuL:2010,BuscemiM:2008}; and more recently
  Feng et al. provide a symbolic bisimulation for quantum processes \cite{feng2014symbolic}.
-\TODO{check next sentence}
-All the above works are based on models  definitely different from ours, and none of them allows system to be as much parameterised as open pNets; this additional expressiveness due to the open and symbolic nature of our constructs.
+All the above works, did not give a complete approach for verification \TODO{Ludo}, and the models on which these works based are definitely different from ours.
 
@@
 \label{section:conclusion}
- pNets (Parameterised Networks of Automata) is a formalism adapted to the representation of the behaviour of  parallel or distributed systems.
-One  strength of pNets is their parameterised nature, making them suitable for to the representation of systems of arbitrary size, and making the modelling of parameterised system possible.
+ pNets (Parameterised Networks of Automata) is a formalism adapted to the representation of the behaviour of a parallel or distributed systems.
+One  strength of pNets is their parameterised nature, making them adapted to the representation of systems of arbitrary size, and making the modelling of parameterised system possible.
 Parameters are also crucial to reason on interaction protocols that can address one entity inside an indexed set of processes.
@@
 VCE is the specification and verification platform that uses pNets as an intermediate representation.
-\TODO{Eric: short mentions and links to our tools and examples papers}
+\ERIC{We have developed tool support for computing the
+symbolic semantics in term of open automata; this is presented in \cite{QBMZ-AVOCS18,qin:hal-01823507}, together with a case-study based on the on-board control software of satellites.
+In \cite{bliudze:hal-02143782} we present how to encode reactive systems from the BIP specification language and check their temporal properties using VCE.
+In \cite{hou:hal-02406098,hou:hal-02376147} we describe our strong bisimulation algorithms, with examples in the area of \TODO{HEU, rate, pas d'exemple en dehors de l'equivalence des 2 encodages d'Enable, on n'a jamais publie de case-study de strong FH!}
+}
 
@@
 skeletons, or distributed algorithms.
-We have developed tool support for computing the
-symbolic semantics in term of open automata \cite{QBMZ-AVOCS18}, and have
-developed algorithms to check strong FH-bisimulation and weak FH-bisimulation \cite{hou:hal-02406098,WangMZ:2021}.
+\ERIC{Recently we published preliminary work on methods for checking} weak FH-bisimulation \cite{WangMZ:2021}.
 The challenges here, in the context of our symbolic systems, is not so much algorithmic complexity,
@@
 constructing the weak automata, but searching \emph{on demand} to construct the required weak transitions. 
+\ERIC{We illustrate this approach on a simple error-correcting transport protocol case-study}.
 Beside, we explore in \cite{wang:hal-03126313} more pragmatic approaches using weak bisimulation preserving (pattern-based) 

### 2022-10-07 2016-Weak-FH-Bisim/WeakBisim.tex

--- 2022-10-05 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 
-The definition of this predicate is not constructive but it is easy to build the predicate constructively by brute-force unification of the sub-pNets actions with the corresponding vector actions, possibly followed by a simplification step.
-\TODO{Eric: replace by what we do in the tool, plus cite\{avocs\} }
+% but it is easy to build the predicate constructively by brute-force unification of the sub-pNets actions with the corresponding vector actions, possibly followed by a simplification step.
+\TODO{Check new text}
+
+\ERIC{The definition of this predicate is not constructive. In our tool \cite{qin:hal-01823507}, we construct a logical formula encoding the matching 
+and unification condition involved, and we let an SMT engine (in the current implementation Z3) decide its satisfiability.}
 
@@
 skeletons, or distributed algorithms.
-We have developed tool support for computing the
-symbolic semantics in term of open automata \cite{QBMZ-AVOCS18}, and have
-developed algorithms to check strong FH-bisimulation and weak FH-bisimulation \cite{hou:hal-02406098,WangMZ:2021}.
+
+\ERIC{Recently we published preliminary work on methods for checking} weak FH-bisimulation \cite{WangMZ:2021}.
 The challenges here, in the context of our symbolic systems, are not so much algorithmic complexity,
 as was the case with classical weak bisimulation on finite models, but decidability and termination.
-The naive approach using an explicit construction of the weak transition, may in itself introduce non-termination,
+The naive approach, using an explicit construction of the weak transition, may in itself introduce non-termination,
 so we prefer a direct implementation of the weak bisimulation definition, without
 constructing the weak automata beforehand, but searching \emph{on demand} to construct the required weak transitions. 
+\ERIC{We illustrate this approach on a simple error-correcting transport protocol case-study}.
 Beside, we explore in \cite{wang:hal-03126313} more pragmatic approaches using weak bisimulation preserving (pattern-based) 

### 2022-10-07 2016-Weak-FH-Bisim/WeakBisim.tex
Longue seance avec Rabea

@@
 
-UNlike pNets, open automata are not hierarchical structures, we consider them here as a mathematical structure that is convenient for formal reasoning but not adapted to the definition of a complex and structured system.
+\ERIC{Beware that even if open transitions may look similar to the notion of Transition System Specification \cite{GROOTE1992202,GROOTE20063} and other forms of SOS rules, they are \emph{not} structural rules, but rules defining the behaviour of the global states of the system.
+}
+
+Unlike pNets, open automata are not hierarchical structures, we consider them here as a mathematical structure that is convenient for formal reasoning but not adapted to the definition of a complex and structured system.
 Open transitions are expressed in terms of logics while the communication in pNets is specified as synchronisation vectors that specify synchronised actions.
@@
 an equivalence between the semantics presented in this article and the operational one shown in~\cite{AmeurBoulifa2017} is outside the scope of this article because we focus here on the modelling of holes that were not considered in the previous semantics.
-\TODO{Check}
-It is however easy to see that, in case there is no hole the structure of the open automaton that defines the semantics here is very close to the pLTS that is used in~\cite{AmeurBoulifa2017} to define the semantics even though the formalisms are different.
+\TODO{Check \ERIC{Ok}}
+It is however easy to see that, in case there is no hole the structure of the open automaton that defines the semantics here is very close to the pLTS that is used to define the semantics, even though the formalisms are slightly different.
 
@@
 
-\TODO{Check this paragraph}
+\TODO{Check this paragraph \ERIC{Done}}
 It is important to understand the difference between the red dotted rule and a classical 
 inference rule. They correspond to two different logical levels.
-On one side, classical (black) inference rules act at the mathematical level of the paper proofs. They use  an expressive logic (like any other computer science article).
+On one side, classical (black) inference rules act at the mathematical level of the paper proofs \ERIC{(as e.g.
+the rules in Definition \ref{def:buildweakOT})}.
+They use  an expressive logic (like any other computer science article).
  On the other side, open transition rules (with dotted lines) are logical implications that belong to the open automata algebra.
@@
            \set{\beta}, \Pred\,',\Post\,'}
-          {t \OTarrow {\alpha} t'}\in\mathcal{T}
+          {s \OTarrow {\alpha} s'}\in\mathcal{T}
 \quad\implies\quad
@@
            \set{\beta}\subst{\Post}, \Pred\,'\subst{\Post}\land\Pred,\Post\shortodot\Post\,'}
-         {\raisemath{-2pt}{t \OTarrow {\alpha\subst{\Post}} {t'}}{}}
+         {\raisemath{-2pt}{s \OTarrow {\alpha\subst{\Post}} {s'}}{}}
  \in\mathcal{T}
@@
 \ERIC{The definition of this predicate is not constructive. In our tool \cite{qin:hal-01823507}, we construct a logical formula encoding the matching 
-and unification condition involved, and we let an SMT engine (in the current implementation Z3) decide its satisfiability.}
+and unification condition involved, and we let an SMT engine (in the current implementation Z3 \cite{Johnson:2014:qosa}) decide its satisfiability.}
 
@@
 We first define (in Definition~\ref{def:Non-ObsTau}) systems that cannot observe $\tau$ actions of sub-systems; namely pNets that cannot change their state, or emit an observable action when one of its holes emits a $\tau$ action.
-\TODO{Eric: discuss rel with Vaandrager}
+\TODO{Eric: discuss rel with Vaandrager - ou pas !!}
 
@@
 First rule \WTUn~ adds a $WT_\tau$ loop on each state.
-Rule \WTDeux~ transforms each 3 OTs into WOTs.
-Then consider application of Rule \WTTrois~ on a sequence 3  WOTs.
+Rule \WTDeux~ transforms each 2 OTs into WOTs.
+Then consider application of Rule \WTTrois~ on a sequence of 3  WOTs.
 $\openrule
@@
 For defining a bisimulation relation between weak open automata, two options are possible.
-One option is that we define a simulation similar to the strong simulation but based on open automata, this would look like the FH-simulation but would need to be adapted to weak open transitions.
+One option is that we define a simulation similar to the strong simulation but based on weak open automata, this would look like the FH-simulation but would need to be adapted to weak open transitions.
 Alternatively, we could define directly and classically a weak FH-simulation as a relation between two open automata, relating the open transitions of the first one with the transitions of the weak open automaton derived from the second one.
@@
   Checking that $\mathcal{R}$ is a weak FH-bisimulation means checking, for each of these triples, that each (strong) OT of one the states corresponds to a set of WOTs of the other, using the conditions from Definition \ref{def-Weak-bisim}.
-  We give here one  example: consider the second triple from the table, and transition $SS_3$ from state \texttt{b0}. Its easy to guess that it will correspond to $WI_3(0)$ of state $202$.
+  We give here one  example: consider the second triple from the table, and transition $SS_3$ from state \texttt{b0}.
+Its easy to guess that it will correspond to $WI_3(0)$ of state $202$ (and equivalently state $000$, see Figure \ref{SimpleProtCounter:ImplWOA2}):
 
@@
  Feng et al. provide a symbolic bisimulation for quantum processes \cite{feng2014symbolic}.
-\TODO{check next sentence}
-All the above works are based on models  definitely different from ours, and none of them allows system to be as much parameterised as open pNets; this additional expressiveness due to the open and symbolic nature of our constructs.
+\TODO{check next sentence Ok}
+All the above works are based on models  definitely different from ours, and none of them allows system to be as much parameterised as open pNets; this additional expressiveness is due to the open and symbolic nature of our constructs.
 
@@
 VCE is the specification and verification platform that uses pNets as an intermediate representation.
-\ERIC{We have developed tool support for computing the
+\ERIC{In this platform we have developed tool support for computing the
 symbolic semantics in term of open automata; this is presented in \cite{QBMZ-AVOCS18,qin:hal-01823507}, together with a case-study based on the on-board control software of satellites.
 In \cite{bliudze:hal-02143782} we present how to encode reactive systems from the BIP specification language and check their temporal properties using VCE.
-In \cite{hou:hal-02406098,hou:hal-02376147} we describe our strong bisimulation algorithms, with examples in the area of \TODO{HEU, rate, pas d'exemple en dehors de l'equivalence des 2 encodages d'Enable, on n'a jamais publie de case-study de strong FH!}
+In \cite{hou:hal-02406098,hou:hal-02376147} we describe our strong bisimulation algorithms, with illustration on the equivalence of different encodings of operators.
 }
@@
 The semantics of open pNets relies on the definition of open automata that are automata with holes and parameters, but no hierarchy.
-\TODO{check this sentence} Open atomata are a flattened view of the pNet; their behaviour is expressed as open transitions that allow for a more semantic interpretation of parameters than pNets.
-Open automata are  labelled transition systems with parameters and holes, a notion that is useful to define semantics, but makes less sense when modelling a system, compared to pNets.
+\TODO{check this sentence - \ERIC{nouvelle proposition:}} Open automata are a flattened view of the pNet; their behaviour is expressed as open transitions that allow for a more semantic interpretation of \ERIC{process parameters (holes)} than pNets.
+In the end, open automata are  labelled transition systems with parameters and holes, a notion that is useful to define semantics, but makes less sense \ERIC{for the high level modelling of a system}, compared to pNets.
 To be precise, it is on open automata that we define our FH-bisimilarity relations.
@@
 Our strong  FH-bisimilarity is compositional  in the sense that FH-bisimilarity is maintained when composing processes.
-We also identified a simple and realistic condition on the semantics of non-observable actions that allows weak FH-bisimilarity to be also compositional \TODO{Eric: recall on rule formats}.
+We also identified a simple and realistic condition on the semantics of non-observable actions that allows weak FH-bisimilarity to be also compositional \TODO{Eric: recall on rule formats \ERIC{Non, vu ce qu'on a ecrit dans l'intro}}.
 Overall we believe that this article paved the way for a solid theoretical foundation for compositional verification of parallel and distributed systems.
@@
 For any open transition $OT_{px}$, since
-       	$(t_p,u|\Pred_{p,u})\in\mathcal{R}'$ there exists an indexed set of open transitions
+       	$(t_p,u|\Pred\,'_{p,u})\in\mathcal{R}'$ there exists an indexed set of open transitions
        	$OT_{pxy}^{y\in Y} \subseteq \mathcal{T}_3$:

### 2022-10-07 2016-Weak-FH-Bisim/WeakBisim.tex
typos

@@
 We develop here a semantics for a model of interacting processes with parameters and holes. 
-Our approach is originally inspired from Structured Operational Semantics with conditional premisses as in \cite{GROOTE1993263,VANGLABBEEK2004229}.
+Our approach is originally inspired from Structured Operational Semantics with conditional premises as in \cite{GROOTE1993263,VANGLABBEEK2004229}.
 But we aim at a more constructive and implementable approach to compute the semantics (intuitively transitions including first order predicates) and to 
@@
 \item	The  rule \TrDeux\ deals with pNet nodes: for each possible
-	synchronisation vector (of index $k$) applicable to the rule subject, the premisses
+	synchronisation vector (of index $k$) applicable to the rule subject, the premises 
 	include one {\em open transition} for each sub-pNet involved, one possible
@@
 Among the approaches for modelling open systems, one can cite  \cite{Beohar:2020} that uses transition conditions depending on an external environment, and introduce bisimulation relations based on this approach.
-The approach of  \cite{Beohar:2020} is
-  highly based on logics and their bisimulation theory is richer than ours in this aspect, while our theory is highly structural and focuses on relation between structure and equivalence.
+The approach of  \cite{Beohar:2020} is  highly based on logics and their bisimulation theory is richer than ours in this aspect, while our theory is highly structural and focuses on relation between structure and equivalence.
 Also, we see composition as a structural operation putting systems together, and do not focus on the modelling of an unknown outside world.
@@
 There is also a clear relation with the seminal works on rule formats for Structured Operational Semantics, e.g.
-DeSimone format, GSOS, and conditional rules with or without negative premisses \cite{deSimone85,Bloom:1995,GROOTE1992202,VANGLABBEEK2004229}.
+DeSimone format, GSOS, and conditional rules with or without negative premises \cite{deSimone85,Bloom:1995,GROOTE1992202,VANGLABBEEK2004229}.
 The Open pNets model provides a way to define operators similar to these rules formats, but with quite different aim and approach.
 A formal comparison would be interesting, though not trivial.
-What we can say easily is that: the pNet format syntactically encompasses  De Simone, GSOS, and conditional premisses rules.
+What we can say easily is that: the pNet format syntactically encompasses  De Simone, GSOS, and conditional premises rules.
 Then our compositionality result is more powerful than their classical results, but this is not a surprise, as we rely on a (sufficient) syntactic hypothesis on a particular system, rather than the general rules defining an operator.
-Last, we intentionally do not accept negative premisses, that would be more  to put into practice in our implementation.
+Last, we intentionally do not accept negative premises, that would be more  to put into practice in our implementation.
 This extension could be studied in future work.

### 2022-10-09 2016-Weak-FH-Bisim/JLAMP-AnswerToReviewers.tex
Create JLAMP-AnswerToReviewers.tex

\documentclass[10pt]{article}
\usepackage[latin1]{inputenc} 
\usepackage{alltt,url}
%% Old ttbox definition without frame:
\newenvironment{ttbox}{\begin{alltt}\small\tt}%
                      {\end{alltt}}
\usepackage{color}
\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
\newcommand{\NOTE}[1]{\textcolor{blue}{\textbf{[NOTE:#1]}}}
\newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
\thispagestyle{empty}
\addtolength{\textheight}{2cm}
\begin{document}
\section*{Answer to reviewers }
\subsection*{Submission to Journal of Logical and Algebraic Methods in Programming}
\medskip
\begin{ttbox}
Title: Compositional equivalences based on Open pNets
Authors: R. Ameur-Boulifa, L. Henrio, and E. Madelaine
\end{ttbox}
\bigskip
%\subsubsection*{Letter to Reviewers and Editors}
Dear reviewers and editors,

\ERIC{P4, *say that this is like in Symbolic Bisimulation
\begin{quote}Pas sur du tout, je bosse encore la-dessus...
\end{quote}}

\ERIC{P4, *Any relations with the conditions on SOS rule formats guaranteeing compositionality of weak bisimilarity?
\begin{quote} non je n'ai pas repondu ici... voir paragraph page precedente, est-ce suffisant "
\end{quote}}

\ERIC{P14, *Is your definition a combination of De Simone FH-bisimulation and Hennessy and Lin's symbolic bisimulation?
\begin{quote}
Je n'ai pas redige ca... mais l'idee pourrait etre que en gros oui, et en y ajoutant le formalisme synch vecteurs de Arnold et Nivat, 
mais que notre approache est sensiblement differente, puisque plus syntaxique, pour permettre le developpement de representation finies, d'algorithmes, et d'outils...
\ned{quote}

\ERIC{P17, *What is the comoplexity of this "brute force approach"?
\begin{quote}
le paragraph existant etait difficilement comprehensible et loin de notre implementation dans l'outil. J'ai remplace par quelque chose de plus factuel:
"The definition of this predicate is not constructive. In our tool [39], we construct a logical formula encoding the matching and unification conditions involved, and let an SMT engine (in the current implementation Z3 [30]) decide its satisfiability"
\end{quote}}

\ERIC{page 36, *It'd be a good idea to give links to software tools implementing your approach and to examples case-studies
\begin{quote}
J'ai ajoute 7 ligns ici: "In this platform [...] different encodings of operators".
C'est un peu faible parceque 1) les outils de sont pas encore accessibles en ligne (ca aurait du etre l'achevement du stage de Slava...), et 2) on n'a pas de papier sur un vrai "use-case', a part le AVOCS sur le satellite, mais qui ne fait pas de bisimulation, juste des proprietes temporelles.
\end{quote}}

\begin{flushright}
  Best Regards,\\
  Rab\'ea Ameur-Boulifa, Ludovic Henrio, and Eric Madelaine
\end{flushright}
\end{document}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2022-10-10 2016-Weak-FH-Bisim/WeakBisim.tex
papier Larsen
statechart

@@
 exposes a single resulting global action.
+\RAB{Pas sur au bon endroit mais -- The pNets model is hierarchical in the structure of the processes, in contrast to the Statecharts formalism \cite{Harel:87}, which is widely used to model high-level behaviour,  that organises the states in a hierarchy.}
 
@@
 the actions it exposes.
+\RAB{In the same vein as for context systems \cite{Larsen:91}, pNets is a formalism for modular and possibly incomplete  description of concurrent systems.
+The theory of contexts relies on a form of rewrite rules, while the pNets on the notion of automata.
+}
 \TODO{Rabea: look for papers by Larsen end Liu on context systems, and Larsen and Huttel on static constructs}
@@
 Defining properly the interaction between a logical formulae in the action and the logics of the pNet composition seems very difficult.
+\RAB{This is despite the fact that our approach can support alternative techniques for overcoming the state-space-explosion problem  as quotienting technique for compositional model checking  \cite{Larsen:91}.}
 \TODO{Rabea: look for "quotienting techniques"}

### 2022-10-12 2016-Weak-FH-Bisim/WeakBisim.tex
morning pass

@@
 synchronisation between the parameterised actions of a subset of the sub-trees.
+The pNets model is hierarchical in the structure of the processes, in contrast to the Statecharts formalism \cite{Harel:87}, which is widely used to model high-level behaviour,  that organises the states in a hierarchy.
+\LUDO{I moved this sentence here}
 
@@
 %$a$ is not already an indexed set.}
+
+\RAB{In the same vein as for context systems \cite{Larsen:91}, pNets is a formalism for modular and possibly incomplete  description of concurrent systems.
+The two formalisms are however different as the theory of contexts relies on a form of rewrite rules, while  pNets rely on parametric automata to express the system behaviour.
+}
+\TODO{Rabea: look for papers by Larsen end Liu on context systems, and Larsen and Huttel on static constructs}
 
@@
 exposes a single resulting global action.
-\RAB{Pas sur au bon endroit mais -- The pNets model is hierarchical in the structure of the processes, in contrast to the Statecharts formalism \cite{Harel:87}, which is widely used to model high-level behaviour,  that organises the states in a hierarchy.}
 
@@
 the actions it exposes.
-\RAB{In the same vein as for context systems \cite{Larsen:91}, pNets is a formalism for modular and possibly incomplete  description of concurrent systems.
-The theory of contexts relies on a form of rewrite rules, while the pNets on the notion of automata.
-}
-\TODO{Rabea: look for papers by Larsen end Liu on context systems, and Larsen and Huttel on static constructs}
 
@@
 an equivalence between the semantics presented in this article and the operational one shown in~\cite{AmeurBoulifa2017} is outside the scope of this article because we focus here on the modelling of holes that were not considered in the previous semantics.
-\TODO{Check \ERIC{Ok}}
 It is however easy to see that, in case there is no hole the structure of the open automaton that defines the semantics here is very close to the pLTS that is used to define the semantics, even though the formalisms are slightly different.
@@
 
-\TODO{Check this paragraph \ERIC{Done}}
 It is important to understand the difference between the red dotted rule and a classical 
 inference rule. They correspond to two different logical levels.
-On one side, classical (black) inference rules act at the mathematical level of the paper proofs \ERIC{(as e.g.
-the rules in Definition \ref{def:buildweakOT})}.
+On one side, classical (black) inference rules act at the mathematical level of the paper proofs (as e.g.
+the rules in Definition \ref{def:buildweakOT}).
 They use  an expressive logic (like any other computer science article).
@@
 % but it is easy to build the predicate constructively by brute-force unification of the sub-pNets actions with the corresponding vector actions, possibly followed by a simplification step.
-\TODO{Check new text}
+\TODO{Check new text \LUDO{OK}}
 
@@
  Feng et al. provide a symbolic bisimulation for quantum processes \cite{feng2014symbolic}.
-\TODO{check next sentence Ok}
 All the above works are based on models  definitely different from ours, and none of them allows system to be as much parameterised as open pNets; this additional expressiveness is due to the open and symbolic nature of our constructs.

### 2022-10-12 2016-Weak-FH-Bisim/JLAMP-AnswerToReviewers.tex
Meeting notes

@@
 
-\ERIC{P4, *say that this is like in Symbolic Bisimulation
+\ERIC{P4, *say that this is like in Symbolic Bisimulation}
 \begin{quote}Pas sur du tout, je bosse encore la-dessus...
-\end{quote}}
+\end{quote}
 
-\ERIC{P4, *Any relations with the conditions on SOS rule formats guaranteeing compositionality of weak bisimilarity?
+\ERIC{P4, *Any relations with the conditions on SOS rule formats guaranteeing compositionality of weak bisimilarity?}
 \begin{quote} non je n'ai pas repondu ici... voir paragraph page precedente, est-ce suffisant "
-\end{quote}}
+\end{quote}
 
@@
 mais que notre approache est sensiblement differente, puisque plus syntaxique, pour permettre le developpement de representation finies, d'algorithmes, et d'outils...
-\ned{quote}
+\end{quote}
 
-\ERIC{P17, *What is the comoplexity of this "brute force approach"?
+\ERIC{P17, *What is the comoplexity of this "brute force approach"?}
 \begin{quote}
@@
 In our tool [39], we construct a logical formula encoding the matching and unification conditions involved, and let an SMT engine (in the current implementation Z3 [30]) decide its satisfiability"
-\end{quote}}
+\end{quote}
 
-\ERIC{page 36, *It'd be a good idea to give links to software tools implementing your approach and to examples case-studies
+\ERIC{page 36, *It'd be a good idea to give links to software tools implementing your approach and to examples case-studies}
 \begin{quote}
@@
 C'est un peu faible parceque 1) les outils de sont pas encore accessibles en ligne (ca aurait du etre l'achevement du stage de Slava...), et 2) on n'a pas de papier sur un vrai "use-case', a part le AVOCS sur le satellite, mais qui ne fait pas de bisimulation, juste des proprietes temporelles.
-\end{quote}}
+\end{quote}
 

### 2022-10-12 2016-Weak-FH-Bisim/WeakBisim.tex
Meeting notes

@@
 naturally action terms will use data expressions as sub-terms\footnote{In our tools, we use datatypes for the different kinds of terms.
-In this article, we use different sets of variables for variables and terms of different kinds.}.
+In this article, we use different sets of variables for  terms of different kinds.}.
 The function $\vars(t)$ identifies the set of variables in a term
 $t\in\AlgT$.
-\TODO{check footnote}
 
@@
 synchronisation between the parameterised actions of a subset of the sub-trees.
-The pNets model is hierarchical in the structure of the processes, in contrast to the Statecharts formalism \cite{Harel:87}, which is widely used to model high-level behaviour,  that organises the states in a hierarchy.
-\LUDO{I moved this sentence here}
+The pNets model is hierarchical in the structure of the processes, in contrast to the Statecharts formalism \cite{Harel:87}, which is widely used to model high-level behaviour,  that organises the states (but not processes) in a hierarchy.
 
@@
 Synchronisation vectors are identified modulo renaming of variables that appear in their 
-action terms, e.g. the vectors $<a(x),b(x)>\to\tau$ and $<a(y),b(y)>\to\tau$ are equivalent. \TODO{check if more explanation is needed here}
+action terms, e.g. the vectors $<a(x),b(x)>\to\tau$ and $<a(y),b(y)>\to\tau$ are equivalent.
 \end{definition}
@@
 % but it is easy to build the predicate constructively by brute-force unification of the sub-pNets actions with the corresponding vector actions, possibly followed by a simplification step.
-\TODO{Check new text \LUDO{OK}}
-
-\ERIC{The definition of this predicate is not constructive. In our tool \cite{qin:hal-01823507}, we construct a logical formula encoding the matching 
-and unification condition involved, and we let an SMT engine (in the current implementation Z3 \cite{Johnson:2014:qosa}) decide its satisfiability.}
+
+The definition of this predicate is not constructive. In our tool \cite{qin:hal-01823507}, we construct a logical formula encoding the matching 
+and unification condition involved, and we let an SMT engine (in the current implementation Z3 \cite{Johnson:2014:qosa}) decide its satisfiability.
 
@@
 Defining properly the interaction between a logical formulae in the action and the logics of the pNet composition seems very difficult.
-\RAB{This is despite the fact that our approach can support alternative techniques for overcoming the state-space-explosion problem  as quotienting technique for compositional model checking  \cite{Larsen:91}.}
-\TODO{Rabea: look for "quotienting techniques"}
+Quotienting nd decomposition techniques \cite{Larsen:91} seem closer to our approach as they propose to 
+overcome the state-space-explosion problem by decomposing formulas to be verified according to the process composition. 
+However these techniques are expressed in a very different setting from ours and it is difficult to precisely relate them to the more structural and parameterised point of view we adopt here.
+We could try to apply such decomposition techniques to open pNets, but deriving a decomposition  for systems synchronised in a very parameterised way like we do requires further investigations.
 

### 2022-10-12 2016-Weak-FH-Bisim/WeakBisim.tex
refs and ...

@@
 %%% \TODO{voisr si on redefinit les bigotimes pour prendre des maps et retourner des maps au lieu des substitutions (et on englobe dans une subst a la fin)}
-%
 %%% \TODO{prendre soin des posts sur les actions partout}
@@
 Compositionality of bisimilarity in our model comes from the specification of the interactions, including actions of the holes. 
-\ERIC{This is quite different from the works on contextual equivalences, e.g. \cite{Larsen}; we will give more details on this in section \ref{sec:RW}.}
+\ERIC{This is quite different from the works on contextual equivalences, e.g. \cite{Larsen:91}; we will give more details on this in section \ref{sec:RW}.}
 In pNets, synchronisation vectors define the possible interactions between the pNet that fills the hole and the surrounding pNets.
@@
 expressions $\AlgB$ ($\AlgB\subseteq\AlgE$), 
-and a set of action expressions $\AlgE$ called the action algebra
+and a set of action expressions  called the action algebra
 $\AlgA$, with $\AlgA\subseteq\AlgT,
@@
 
-Thus, we let $\gamma$ range over sequences of action terms and use $\dotcup$ as the concatenation operator that appends sequences of action terms: given two sequences of action terms  $\gamma\dotcup\gamma '$ concatenates the two sequences.
+Thus, we let $\gamma$ range over sequences of action terms and use $\dotcup$ as the concatenation operator that appends sequences of action terms: given two sequences of action terms  $\gamma\dotcup\gamma'$ concatenates the two sequences.
 The operation is lifted to indexed sets of sequences:   at each index $i$, $\set {\gamma_1}\dotcup \set {\gamma_2}$ concatenates the sequences of actions at index $i$ of $\set{\gamma_1}$ and the one at index $i$ of $\set {\gamma_2}$\footnote{One of the two sequences is empty when $i\not \in \dom(\set{\gamma_1})$ or $i\not \in \dom(\set{\gamma_2})$ .}.

### 2022-10-12 2016-Weak-FH-Bisim/WeakBisim.tex
add mcrl2 + ccl + handle some todos

@@
 
-The disjoint union on sets is $\uplus$ and we only use $A\uplus B$ when the index sets of the $A$ and $B$ are disjoints. We extend it to  disjoint union  of indexed 
-sets defined by the merge of the 
-two sets provided they are indexed over disjoint families.
+The disjoint union on sets is $\uplus$ and we only use $A\uplus B$ when $A$ and $B$ are disjoint.
+We extend it to   union  of indexed sets provided they are indexed over disjoint families; is $\uplus$  is then defined by the merge of the
+two sets.
 The elements
@@
 
-\TODO{Ludo: a sentence on inspiration from RdS, and forward link to related work}
-
 The semantics of open pNets will be defined  as an open automaton. An open
@@
 We also adopt a semantics and logical interpretation of the automata that intuitively can be stated as follows: ``if a transition belongs to an open automaton, any refinement of this transition also belongs to the automaton''.
+\LUDO{Our open automata are clearly inspired by the work  of de Simone on formatting of SOS rules~\cite{deSimone85}.
+A precise comparison with related works can be found in Section~\ref{sec:RW}.}
 
@@
 
+\begin{example}
+The simulation of one transition by many others is one non-standard aspect of this definition. This is made necessary by the parameterised nature of our model. Consider the open transition:
+\[ \openrule
+         {
+           \set{\beta}, \True,\subst{y\leftarrow x}}
+          {s \OTarrow {\alpha(x)} s'}\]
+Bisimulation should allow it to be matched by the two following ones (depending on the value of $x$):
+\[ \openrule
+         {
+           \set{\beta}, x\geq 0,\subst{y\leftarrow x}}
+          {s \OTarrow {\alpha(x)} s'}
+\qquad
+\openrule
+         {
+           \set{\beta}, x<0,\subst{y\leftarrow x}}
+          {s \OTarrow {\alpha(x)} s'}
+\]
+This example illustrates the necessity of multiple transitions in the definition of bisimulation in a naive and minimalistic way.
+It can easily be extended into a non-trivial example with more states and different usage of the variables.
+\end{example}
+
 \begin{thm}[FH-bisimularity is an equivalence]\label{thm-equiv} FH-bisimilarity is 
@@
 The second statement ensures that there cannot be in the open automaton other transitions that would be able to observe a $\tau$ action from a hole: statement (2) states that all the open transitions where a hole does  a $\tau$ action must be of the shape given in statement (1).
-The condition $J=\{j\}$ is a bit restrictive, it could safely be replaced by $\forall j\in J.\, \beta_j=\tau$, allowing the other holes to perform $\tau$ transitions too (because these $\tau$ actions cannot be observed).
+In this second statement, the condition $J=\{j\}$ is a bit restrictive, it could safely be replaced by $\forall j\in J.\, \beta_j=\tau$, allowing the other holes to perform $\tau$ transitions too (because these $\tau$ actions cannot be observed).
+This possible synchronisation of $\tau$ actions would not be a problem as condition 1 still ensures that each process can do a $\tau$ separately.
 
@@
 Defining properly the interaction between a logical formulae in the action and the logics of the pNet composition seems very difficult.
-Quotienting nd decomposition techniques \cite{Larsen:91} seem closer to our approach as they propose to 
+Quotienting and decomposition techniques \cite{Larsen:91,LaveauxWillemse:ICE21} seem closer to our approach as they propose to 
 overcome the state-space-explosion problem by decomposing formulas to be verified according to the process composition. 
 However these techniques are expressed in a very different setting from ours and it is difficult to precisely relate them to the more structural and parameterised point of view we adopt here.
-We could try to apply such decomposition techniques to open pNets, but deriving a decomposition  for systems synchronised in a very parameterised way like we do requires further investigations.
+We could try to apply such automatic decomposition techniques to open pNets, but deriving a decomposition  for systems synchronised in a very parameterised way like we do requires further investigations.
+Both parallel composition~\cite{Larsen:91} and mCRL2~\cite{LaveauxWillemse:ICE21} feature a concrete verification setting where decomposition is useful, while open automata provide a more general setting that could be used to represent both frameworks and hopefully generalise process decomposition results of \cite{Larsen:91,LaveauxWillemse:ICE21}.
 
@@
 VCE is the specification and verification platform that uses pNets as an intermediate representation.
-\ERIC{In this platform we have developed tool support for computing the
+{In this platform we have developed tool support for computing the
 symbolic semantics in term of open automata; this is presented in \cite{QBMZ-AVOCS18,qin:hal-01823507}, together with a case-study based on the on-board control software of satellites.
@@
 The semantics of open pNets relies on the definition of open automata that are automata with holes and parameters, but no hierarchy.
-\TODO{check this sentence - \ERIC{nouvelle proposition:}} Open automata are a flattened view of the pNet; their behaviour is expressed as open transitions that allow for a more semantic interpretation of \ERIC{process parameters (holes)} than pNets.
-In the end, open automata are  labelled transition systems with parameters and holes, a notion that is useful to define semantics, but makes less sense \ERIC{for the high level modelling of a system}, compared to pNets.
-To be precise, it is on open automata that we define our FH-bisimilarity relations.
+Open automata are a flattened view of the pNet; their behaviour is expressed as open transitions that allow for a more semantic interpretation of process parameters (holes) than pNets.
+In the end, open automata are  labelled transition systems with parameters and holes, a notion that is useful to define semantics, but makes less sense for the high level modelling of a system, compared to pNets.
+Open automata is the formalism that makes it possible to define FH-bisimilarity.
 
 This article defines a strong and a weak bisimulation relation that are adapted to parameterised systems and hierarchical composition.
-Our FH-bisimulation principle handles pNet parameters in the sense that two states might be or not in relation depending on the value of parameters.
-Our strong  FH-bisimilarity is compositional  in the sense that FH-bisimilarity is maintained when composing processes.
-We also identified a simple and realistic condition on the semantics of non-observable actions that allows weak FH-bisimilarity to be also compositional \TODO{Eric: recall on rule formats \ERIC{Non, vu ce qu'on a ecrit dans l'intro}}.
+FH-bisimulation  handles pNet parameters in the sense that two states might be or not in relation depending on the value of parameters.
+Strong  FH-bisimilarity is compositional  in the sense that it is maintained when composing processes.
+We also identified a simple and realistic condition on the semantics of non-observable actions that allows weak FH-bisimilarity to be also compositional.
 Overall we believe that this article paved the way for a solid theoretical foundation for compositional verification of parallel and distributed systems.
 
+\LUDO{
 pNets support the refinement checking at the automaton level through a simulation approach, with symbolic evaluation of
 the guards and transitions. 
- The definition of simulation on open automata should be  stronger than a strict simulation since it matches a transition with a family of transitions.
-Such a relation should be able to check the refinement between two open automata with the same level of abstraction but specified differently, for example, by duplicating states, removing transitions, strengthening guards, modifying variables.
+ The definition of simulation on open automata should be  stronger than a classical simulation since it matches a transition with a family of transitions.
+Such a relation should be able to check the refinement by taking into account state duplication,  transition removal,  guard strengthening,  variable modification.
 Additionally, composition of
@@
 A useful simulation relation  should thus support the  comparison of automata that do not have the same number of holes.
-Designing such a simulation relation is a non-trivial extension of this work that we are investigating.
-
-We are currently extending this work,  looking at further properties of FH-bisimulation, but also
+Designing such a simulation relation is a non-trivial extension that we leave for future work.}
+
+We are currently  looking at further properties of FH-bisimulation, but also
 the relations with existing equivalences on both closed and open systems. In particular, our model being significantly different from those considered in \cite{IngolfsdottirL:2001}, it
@@
 
-\ERIC{Recently we published preliminary work on methods for checking} weak FH-bisimulation \cite{WangMZ:2021}.
+{Recently we published preliminary work on methods for checking} weak FH-bisimulation \cite{WangMZ:2021}.
 The challenges here, in the context of our symbolic systems, are not so much algorithmic complexity,
@@
 constructing the weak automata beforehand, but searching \emph{on demand} to construct the required weak transitions. 
-\ERIC{We illustrate this approach on a simple error-correcting transport protocol case-study}.
+{We illustrate this approach on a simple error-correcting transport protocol case-study}.
 Beside, we explore in \cite{wang:hal-03126313} more pragmatic approaches using weak bisimulation preserving (pattern-based) 

### 2022-10-17 2016-Weak-FH-Bisim/WeakBisim.tex
similarity with symbolic bisimulations
en page 4
comments reu

@@
 Instead, bisimulation for open automata  relies on the simulation of each open transition of one automaton by \emph{a set of} open transitions of the other one, that should cover all the
-cases where the original transition can be triggered. \TODO{Eric: is this like in symbolic bisimulation ?}
+cases where the original transition can be triggered. %\TODO{Eric: is this like in symbolic bisimulation ?}
+\ERIC{This is similar to the early and late symbolic bisimulation equivalences for value-passing CCS \cite{HENNESSY:1995}, though we need more general definitions in our setting.}
 
@@
 
-Two open automata are FH-bisimilar if there exists an FH-bisimulation that relates their initial states\footnote{I.e., the predicate relation associated to the initial states is \True.}.
+Two open automata are FH-bisimilar if there exists an FH-bisimulation that relates their initial states\footnote{In other words, the predicate relation associated to the initial states is \True.}.
 We call this relation \emph{FH-bisimilarity}.
@@
 \begin{example}
-The simulation of one transition by many others is one non-standard aspect of this definition. This is made necessary by the parameterised nature of our model. Consider the open transition:
+The simulation of one transition by many others is one non-standard aspect of this definition. This is made necessary by the parameterised nature of our model. Consider the following open transition.
 \[ \openrule
@@
            \set{\beta}, \True,\subst{y\leftarrow x}}
-          {s \OTarrow {\alpha(x)} s'}\]
-Bisimulation should allow it to be matched by the two following ones (depending on the value of $x$):
+          {s_1 \OTarrow {\alpha(x)} s_1'}\]
+Bisimulation should allow it to be matched by the two following ones (depending on the value of $x$), to prove the bisimulation $\mathcal{R}=\{(s_1,s_2,\True),(s_1',s_2',\True)\}$
 \[ \openrule
@@
            \set{\beta}, x\geq 0,\subst{y\leftarrow x}}
-          {s \OTarrow {\alpha(x)} s'}
+          {s_2 \OTarrow {\alpha(x)} s_2'}
 \qquad
@@
            \set{\beta}, x<0,\subst{y\leftarrow x}}
-          {s \OTarrow {\alpha(x)} s'}
+          {s_2 \OTarrow {\alpha(x)} s_2'}
 \]

### 2022-10-17 2016-Weak-FH-Bisim/WeakBisim.tex
mucrl2 V0

@@
 Defining properly the interaction between a logical formulae in the action and the logics of the pNet composition seems very difficult.
-Quotienting and decomposition techniques \cite{Larsen:91,LaveauxWillemse:ICE21} seem closer to our approach as they propose to 
-overcome the state-space-explosion problem by decomposing formulas to be verified according to the process composition. 
+mCRL2~\cite{} is another effective model for specifying and proving properties of concurrent systems.
+mCRL2 has an established tool-suite and share similarities with pNets.
+However, pNets feature hierarchical composition with more structure than mCRL2 that composes processes with a parallel operator.
+Synchronisation of processes is expressed very differently; it is difficult to precisely compare multi-actions of mCRL2 with synchronisation vectors of pNets but synchronisation vector ogf pNets enforce a  synchronisation based on the structure while in mCRL2 synchronisation is specified in a versatile, flexible, but less structured way.
+
+Quotienting of process algebras~\cite{Larsen:91} and decomposition techniques for MCRL2~\cite{LaveauxWillemse:ICE21} share similarities with our approach; they propose to 
+overcome the state-space-explosion problem by decomposing formulas to be verified according to the process composition. The decomposed problem must be equivalent to the original one.
 However these techniques are expressed in a very different setting from ours and it is difficult to precisely relate them to the more structural and parameterised point of view we adopt here.

### 2022-10-18 2016-Weak-FH-Bisim/WeakBisim.tex
corrections

@@
 cases where the original transition can be triggered. %\TODO{Eric: is this like in symbolic bisimulation ?}
-\ERIC{This is similar to the early and late symbolic bisimulation equivalences for value-passing CCS \cite{HENNESSY:1995}, though we need more general definitions in our setting.}
+\ERIC{This is similar to the early and late symbolic bisimulation equivalences for value-passing CCS \cite{HENNESSY:1995}, though we use more general definitions in our setting.}
 
 Compositionality of bisimilarity in our model comes from the specification of the interactions, including actions of the holes. 
-\ERIC{This is quite different from the works on contextual equivalences, e.g. \cite{Larsen:91}; we will give more details on this in section \ref{sec:RW}.}
+\ERIC{This is quite different from the works on contextual equivalences, e.g. \cite{Larsen87, Larsen:91}; we will give more details on this in section \ref{sec:RW}.}
 In pNets, synchronisation vectors define the possible interactions between the pNet that fills the hole and the surrounding pNets.
@@
 We also adopt a semantics and logical interpretation of the automata that intuitively can be stated as follows: ``if a transition belongs to an open automaton, any refinement of this transition also belongs to the automaton''.
-\LUDO{Our open automata are clearly inspired by the work  of de Simone on formatting of SOS rules~\cite{deSimone85}.
+\LUDO{Our open automata are clearly inspired by the work  of De Simone on formatting of SOS rules~\cite{deSimone85}.
 A precise comparison with related works can be found in Section~\ref{sec:RW}.}
@@
 \begin{thm}[Congruence]\label{thm-congr-eq}
-	Consider an open pNet:
+	Consider an open pNet \\
 	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
@@
 There is also a clear relation with the seminal works on rule formats for Structured Operational Semantics, e.g.
-DeSimone format, GSOS, and conditional rules with or without negative premises \cite{deSimone85,Bloom:1995,GROOTE1992202,VANGLABBEEK2004229}.
+De Simone format, GSOS, and conditional rules with or without negative premises \cite{deSimone85,Bloom:1995,GROOTE1992202,VANGLABBEEK2004229}.
 The Open pNets model provides a way to define operators similar to these rules formats, but with quite different aim and approach.

### 2022-10-18 2016-Weak-FH-Bisim/WeakBisim.tex
dernieres (?) reponses...

@@
 This approach also allows us to specify a sufficient condition on allowed transitions to make weak bisimilarity compositional; namely it is not possible to synchronise on invisible actions from the holes or prevent them to occur.
-\TODO{Eric: relations with SOS rule formats?}
+\ERIC{This is loosely related to works on the syntactic conditions on SOS rules to check whether weak bisimulation is a congruence for some process algebra operators \cite{GrootVaandrager1992}.
+Our approach is semantical and more global: our sufficient condition applies to a whole (open) system, and is expressed on its open automaton (see Definition \ref{def:non-obspNet}).}
+%\TODO{Eric: relations with SOS rule formats?}
 
@@
  that pioneered this idea.
-\TODO{Eric: combination of RdS, symb bisim, and more}
+\ERIC{Indeed, our definition uses both hypotheses on the behaviour of holes, as in \cite{deSimone85}, and symbolic manipulation of action expressions, as in symbolic bisimulations of \cite{HENNESSY:1995}.
+}
+%\TODO{Eric: combination of RdS, symb bisim, and more}
 

### 2022-10-18 2016-Weak-FH-Bisim/WeakBisim.tex
symbol

@@
 
-Thus, we let $\gamma$ range over sequences of action terms and use $\dotcup$ as the concatenation operator that appends sequences of action terms: given two sequences of action terms  $\gamma\dotcup\gamma'$ concatenates the two sequences.
-The operation is lifted to indexed sets of sequences:   at each index $i$, $\set {\gamma_1}\dotcup \set {\gamma_2}$ concatenates the sequences of actions at index $i$ of $\set{\gamma_1}$ and the one at index $i$ of $\set {\gamma_2}$\footnote{One of the two sequences is empty when $i\not \in \dom(\set{\gamma_1})$ or $i\not \in \dom(\set{\gamma_2})$ .}.
+Thus, we let $\gamma$ range over sequences of action terms and use $\dotcup$ as the concatenation operator that appends sequences of action terms: given two sequences of action terms  $\gamma\oplus\gamma'$ concatenates the two sequences.
+The operation is lifted to indexed sets of sequences:   at each index $i$, $\set {\gamma_1}\oplus \set {\gamma_2}$ concatenates the sequences of actions at index $i$ of $\set{\gamma_1}$ and the one at index $i$ of $\set {\gamma_2}$\footnote{One of the two sequences is empty when $i\not \in \dom(\set{\gamma_1})$ or $i\not \in \dom(\set{\gamma_2})$ .}.
 $[a]$ denotes a sequence with a single element.
@@
 \\
-\set{\gamma}=\set{\gamma_1}\dotcup \set{\gamma_2}\subst{\Post_1}\dotcup\set{\gamma_3}\subst{\Post_2\shortodot \Post_1}\\
+\set{\gamma}=\set{\gamma_1}\dotcup \set{\gamma_2}\subst{\Post_1}\oplus\set{\gamma_3}\subst{\Post_2\shortodot \Post_1}\\
 \alpha'=\alpha\subst{\Post_1}\\
@@
 \displaystyle{
-\set{\gamma}=\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigodot_{j=n}^{0}\Post_{1j}}} \dotcup}\\
-{}~\qquad \displaystyle{\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}} }}
+\set{\gamma}=\bigoplus_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{0} \Post_{1j} } }  \oplus  \vis{\set{\beta_2}\subst{\bigodot_{j=n}^{0}\Post_{1j}}} \oplus}\\
+{}~\qquad \displaystyle{\bigoplus_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}} }}
 \\
@@
 \alpha'=&\alpha\displaystyle{\subst{\bigodot_{j=n+1}^{1}\!\!\Post_{1j}}}\\
-\set{\gamma}=&\mybigdotcup_{i=1}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigodot_{j=n+1}^{1}\Post_{1j}}} \dotcup\\
-& \mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}} }\\
+\set{\gamma}=&\bigoplus_{i=1}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{1} \Post_{1j} } }  \oplus  \vis{\set{\beta_2}\subst{\bigodot_{j=n+1}^{1}\Post_{1j}}} \oplus\\
+& \bigoplus_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}} }\\
 \Pred=&\bigwedge_{i=1}^{n+1}\Pred_{1i}\subst{\bigodot_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j={n+1}}^{1}\Post_{1j}}\land\\ 
@@
 \\\\
-\set{\gamma''}= \vis{\set{\beta_{10}}} \dotcup \set{\gamma}\subst{\Post_{10}}\\
+\set{\gamma''}= \vis{\set{\beta_{10}}} \oplus \set{\gamma}\subst{\Post_{10}}\\
 \Pred\,''\!=\!\Pred_{10}\land\Pred\subst{\Post_{10}}\\\\%\land (\Pred_3\subst{\Post_2})\subst{\Post_{10}}
@@
 \alpha''=&\alpha\subst{\bigodot_{j=n+1}^{1}\Post_{1j}}\subst{\Post_{10}} = \alpha\subst{\bigodot_{j=n+1}^{0}\Post_{1j}}\\
-\set{\gamma''}=&\mybigdotcup_{i=0}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{1} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigodot_{j=n+1}^{1}\Post_{1j}}} \dotcup\\
-&\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}} }
+\set{\gamma''}=&\bigoplus_{i=0}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{1} \Post_{1j} } }  \oplus  \vis{\set{\beta_2}\subst{\bigodot_{j=n+1}^{1}\Post_{1j}}} \oplus\\
+&\bigoplus_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}} }
 \\
@@
 \\
-\set{\gamma}=\set{\gamma_1}\dotcup \set{\gamma_2}\subst{\Post_1}\dotcup\set{\gamma_3}\subst{\Post_2\shortodot \Post_1}\\
+\set{\gamma}=\set{\gamma_1}\oplus \set{\gamma_2}\subst{\Post_1}\oplus\set{\gamma_3}\subst{\Post_2\shortodot \Post_1}\\
 \alpha'=\alpha\subst{\Post_1}
@@
 %where 
-%$\set{\gamma}=\set{\gamma_1} \dotcup \set{\gamma_2} \dotcup \set{\gamma_3}$,
+%$\set{\gamma}=\set{\gamma_1} \oplus \set{\gamma_2} \dotcup \set{\gamma_3}$,
 %$\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}$, and $\Post= ({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K}$
@@
 s=s_{10} \wedge s_{1{(n_1+1)}}\!=s',\quad
-\displaystyle{\set{\gamma_1}= \mybigdotcup_{i=0}^{n_1} \vis{\set{\beta_{1 i}}\subst{\bigodot_{j=i-1}^{0} \Post_{1 j} } }} \\
+\displaystyle{\set{\gamma_1}= \bigoplus_{i=0}^{n_1} \vis{\set{\beta_{1 i}}\subst{\bigodot_{j=i-1}^{0} \Post_{1 j} } }} \\
 \Pred_1\!=\!\bigwedge_{i=0}^{n_1}(\Pred_{1i} \subst{\bigodot_{j=i-1}^{0}\Post_{i j}} ), \quad \Post_1= \bigodot_{i=n_1}^{0} \subst{\Post_{1i}} 
@@
 
-\displaystyle{\set{\gamma_3}= \mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{3 i}}\subst{\bigodot_{j=i-1}^{0} \Post_{3 j} } }}
+\displaystyle{\set{\gamma_3}= \bigoplus_{i=0}^{m_1} \vis{\set{\beta_{3 i}}\subst{\bigodot_{j=i-1}^{0} \Post_{3 j} } }}
 
@@
 \alpha''=&\alpha'\subst{\bigodot_{j=n_2}^{0}\Post_{2j}}\\
-\set{\gamma_2}=&\mybigdotcup_{i=0}^{n_2} \vis{\set{\beta_{2i}}\subst{\bigodot_{j=i-1}^{0} \Post_{2 j} } }  \dotcup  \vis{\set{\beta'}\subst{\bigodot_{j=n_2}^{0}\Post_{2j}}} \dotcup\\
+\set{\gamma_2}=&\bigoplus_{i=0}^{n_2} \vis{\set{\beta_{2i}}\subst{\bigodot_{j=i-1}^{0} \Post_{2 j} } }  \oplus  \vis{\set{\beta'}\subst{\bigodot_{j=n_2}^{0}\Post_{2j}}} \oplus\\
 &
- \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{2i}} \subst{\bigodot_{j=i-1}^{0}\Post\,'_{2j}\shortodot\Post\,'\shortodot\bigodot_{j=n_2}^{0}\Post_{2j}}}
+ \bigoplus_{i=0}^{m_2} \vis{\set{\beta'_{2i}} \subst{\bigodot_{j=i-1}^{0}\Post\,'_{2j}\shortodot\Post\,'\shortodot\bigodot_{j=n_2}^{0}\Post_{2j}}}
 \\
@@
 \alpha''=&\alpha\subst{\!\!\bigodot_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}\\
-\set{\gamma}=&\mybigdotcup_{i=0}^{n_1+n_2} \vis{\set{\beta_{4i}}\subst{\bigodot_{j=i-1}^{0} \Post_{4 j} } }  \dotcup  \vis{\set{\beta'}\subst{\!\!\bigodot_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}}\dotcup \\
-&\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta_{5i}}\subst{\bigodot_{j=i-1}^{0}\Post\,'_{5i}\shortodot\Post\,'\shortodot\!\!\bigodot_{j=n_1+n_2}^{0}\!\!\!\Post_{4i}} }\\
+\set{\gamma}=&\bigoplus_{i=0}^{n_1+n_2} \vis{\set{\beta_{4i}}\subst{\bigodot_{j=i-1}^{0} \Post_{4 j} } }  \oplus  \vis{\set{\beta'}\subst{\!\!\bigodot_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}}\oplus \\
+&\bigoplus_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta_{5i}}\subst{\bigodot_{j=i-1}^{0}\Post\,'_{5i}\shortodot\Post\,'\shortodot\!\!\bigodot_{j=n_1+n_2}^{0}\!\!\!\Post_{4i}} }\\
 \Pred=&
@@
 \alpha=&\alpha'\subst{\bigodot_{j=n}^{0}\Post_{1j}}\\
-\gamma_j^{j\in J'}=&\mybigdotcup_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigodot_{j=n}^{0}\Post_{1j}}} \dotcup\\
-&\mybigdotcup_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}} }
+\gamma_j^{j\in J'}=&\bigoplus_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{0} \Post_{1j} } }  \oplus  \vis{\set{\beta_2}\subst{\bigodot_{j=n}^{0}\Post_{1j}}} \oplus\\
+&\bigoplus_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}} }
 \\
@@
 \\ 
-\set{\gamma'}=\gamma_{j a}^{j\in J_{a}} \dotcup \gamma_{jb}^{j\in J_{b}} \subst{\Post_{OT_a}} \dotcup\gamma_{jc}^{j\in J_{c}} \subst{\Post_{OT_{ b}}\shortodot\Post_{OT_a}}\\
+\set{\gamma'}=\gamma_{j a}^{j\in J_{a}} \oplus \gamma_{jb}^{j\in J_{b}} \subst{\Post_{OT_a}} \oplus\gamma_{jc}^{j\in J_{c}} \subst{\Post_{OT_{ b}}\shortodot\Post_{OT_a}}\\
 \Pred=\Pred_{OT_a}\land\Pred_{OT_{b}}\subst{\Post_{OT_a}}\land \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortodot\Post_{OT_a}}\\
@@
 \end{multline*}
-The three for all statements (on $J_a$, $J_b$ and $J_c$) can be concatenated using $\dotcup$, the list union lifted to indexed sets (if $\gamma=\gamma'$ and $\gamma''=\gamma'''$ then $\gamma\dotcup\gamma''=\gamma'\dotcup\gamma'''$).
+The three for all statements (on $J_a$, $J_b$ and $J_c$) can be concatenated using $\oplus$, the list union lifted to indexed sets (if $\gamma=\gamma'$ and $\gamma''=\gamma'''$ then $\gamma\oplus\gamma''=\gamma'\oplus\gamma'''$).
 \begin{multline*}\forall j\in J_a\uplus J_b\uplus J_c.
-\vis{\beta_{1j}}\dotcup \vis{\beta_{2j}\subst{\Post_{OT_a}}}\dotcup \vis{\beta_{3j} \subst{\Post_2\shortodot\Post_1}}=\\ ~\hspace{5.5cm} \gamma_{j a} \dotcup \gamma_{jb} \subst{\Post_{OT_a}}  \dotcup \gamma_{jc} \subst{\Post_{OT_{b}}\shortodot\Post_{OT_a}}
+\vis{\beta_{1j}}\oplus \vis{\beta_{2j}\subst{\Post_{OT_a}}}\oplus \vis{\beta_{3j} \subst{\Post_2\shortodot\Post_1}}=\\ ~\hspace{5.5cm} \gamma_{j a} \oplus \gamma_{jb} \subst{\Post_{OT_a}}  \oplus \gamma_{jc} \subst{\Post_{OT_{b}}\shortodot\Post_{OT_a}}
 \end{multline*}
@@
 \text{, }
- \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigodot_{i=p-1}^{0}\Post_i}, \\
+ \gamma_j^{j\in J\cap\Holes(Q)}= \bigoplus_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigodot_{i=p-1}^{0}\Post_i}, \\
 {~}\Pred \iff \Pred\,'
@@
 \alpha=&\alpha'{\subst{\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}}\\
-\gamma_j^{j\in J}=&\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{0}\!\! \Post_{1j}}}\dotcup\\&  \vis{\set{\beta_2}\subst{\bigodot_{j=m_1}^{0}\Post_{1j}}} \dotcup  
-{\mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}} }}
+\gamma_j^{j\in J}=&\mybigoplus_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{0}\!\! \Post_{1j}}}\oplus\\&  \vis{\set{\beta_2}\subst{\bigodot_{j=m_1}^{0}\Post_{1j}}} \oplus  
+{\bigoplus_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}} }}
 \\
@@
 \forall l\in L.\,&s_l=s_{0l} \wedge s_{(m_1+1)l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)l}=s'_l\\
-{(\gamma_j')}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}=&\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{0}\!\!\Post\,'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigodot_{j=m_1}^{0}\Post\,'_{1j}}}} \dotcup\\
-& \mybigdotcup_{i=0}^{m_2}
+{(\gamma_j')}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}=&\displaystyle{\bigoplus_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{0}\!\!\Post\,'_{1j}}}\oplus  \vis{\set{\beta_{2}}\subst{\bigodot_{j=m_1}^{0}\Post\,'_{1j}}}} \oplus\\
+& \bigoplus_{i=0}^{m_2}
 \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\!\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}} }
@@
 %Concerning $\gamma'_{j_0}$ we have:
-%\[\gamma'_{j_0}=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{{\alpha_{1i}}\subst{\bigodot_{j=i-1}^{0}\!\!\Post'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigodot_{j=m_1}^{0}\Post'_{1j}}}} \dotcup\\
-%~~\qquad \mybigdotcup_{i=0}^{m_2}
+%\[\gamma'_{j_0}=\displaystyle{\bigoplus_{i=0}^{m_1} \vis{{\alpha_{1i}}\subst{\bigodot_{j=i-1}^{0}\!\!\Post'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigodot_{j=m_1}^{0}\Post'_{1j}}}} \dotcup\\
+%~~\qquad \bigoplus_{i=0}^{m_2}
 %\vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigodot_{j=m_1}^{0}\!\!\Post'_{1j}} }\]
@@
 \alpha_k=&\alpha'_{n_k}{\subst{\bigodot_{j=n_k-1}^{n'_{k}}\!\!\Post\,''_{j}}}\\
-{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=&{\mybigdotcup_{i=n'_{k}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigodot_{l=i-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}\dotcup \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigodot_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}} \dotcup\\
-&\mybigdotcup_{i=n_k+1}^{n'_{k+1}-1}
+{\gamma_{kj}^{j\in J\cap\Holes(Q)} }=&{\bigoplus_{i=n'_{k}}^{(n_k\!-\!1)} \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}}\subst{\bigodot_{l=i-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}\oplus \vis{{\beta_{n_k j}^{j\in J\cap\Holes(Q)}}\subst{\bigodot_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}}}} \oplus\\
+&\bigoplus_{i=n_k+1}^{n'_{k+1}-1}
 \vis{{\beta_{ij}^{j\in J\cap\Holes(Q)}} \subst{\bigodot_{l=i-1}^{n_k\!+\!1}\!\Post\,''_{l}\shortodot\Post\,''_{n_k}\shortodot\!\!\bigodot_{l=n_k-1}^{n'_{k}}\!\!\!\Post\,''_{l}} }\\
@@
 \Pred_\beta &\iff& \gamma_{j_0}\!=\!
-\mybigdotcup_{p=0}^{p=n_1+n_2+2}
+\bigoplus_{p=0}^{p=n_1+n_2+2}
 \vis{\alpha'_{p}\subst{\bigodot_{j=p-1}^{0}\!\!\Post_{j}}}\\
 %&\iff&\gamma_{j_0}=
-%\mybigdotcup_{p=0}^{p=n_1+n_2+2}
+%\bigoplus_{p=0}^{p=n_1+n_2+2}
 %\vis{\alpha_{p}\subst{\bigodot_{j=p-1}^{n'_p}\!\!\Post_{j}}\subst{\bigodot_{j=n'_p-1}^{0}\!\!\Post_{j}}}\\
@@
 \[  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) \qquad\text{trivial}\]
-\[ \gamma_j^{j\in J\cap\Holes(Q)}= \mybigdotcup_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigodot_{i=p-1}^{0}\Post_i)}\]
+\[ \gamma_j^{j\in J\cap\Holes(Q)}= \bigoplus_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigodot_{i=p-1}^{0}\Post_i)}\]
 Indeed we have:
@@
 \begin{split}
-\gamma_j^{j\in J}=&\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{0}\!\!
-\Post_{1j}}}\dotcup  \vis{\set{\beta_2}\subst{\bigodot_{j=m_1}^{0}\Post_{1j}}} \dotcup\\& \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}} }\\
+\gamma_j^{j\in J}=&\bigoplus_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{0}\!\!
+\Post_{1j}}}\oplus  \vis{\set{\beta_2}\subst{\bigodot_{j=m_1}^{0}\Post_{1j}}} \oplus\\& \bigoplus_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}} }\\
 \end{split}\end{equation*}
@@
 \begin{split}
-\gamma_j^{j\in J\cap \Holes(Q)}&=\mybigdotcup_{i=0}^{m_1} \vis{\set{(\beta_{1i}')}\subst{\bigodot_{j=i-1}^{0}\!\!
-\Post''_{1j}}}\dotcup  \vis{\set{\beta'_2}\subst{\bigodot_{j=m_1}^{0}\Post''_{1j}}} \dotcup\\&\qquad\qquad \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta'_{3i}} \subst{\bigodot_{j=i-1}^{0}\!\Post''_{3j}\shortodot\Post''_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post''_{1j}} }\\
-&=\mybigdotcup_{k=0}^n \left( \mybigdotcup_{i=n'_k}^{n'_{k+1}-1}\vis{\beta_{ij}^{j\in J\cap \Holes(Q)}\subst{\bigodot_{j=i-1}^{n'_k}\!\!\Post''_{j}\bigodot_{j=n'_k-1}^{0}\!\!\Post''_{j}}}\right)\\
-&=\mybigdotcup_{k=0}^n \left( \gamma_{kj}^{j\in J\cap \Holes(Q)}\subst{\bigodot_{j=k-1}^{0}\!\!\Post_{k}}\right)
+\gamma_j^{j\in J\cap \Holes(Q)}&=\bigoplus_{i=0}^{m_1} \vis{\set{(\beta_{1i}')}\subst{\bigodot_{j=i-1}^{0}\!\!
+\Post''_{1j}}}\oplus  \vis{\set{\beta'_2}\subst{\bigodot_{j=m_1}^{0}\Post''_{1j}}} \oplus\\&\qquad\qquad \bigoplus_{i=0}^{m_2} \vis{\set{\beta'_{3i}} \subst{\bigodot_{j=i-1}^{0}\!\Post''_{3j}\shortodot\Post''_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post''_{1j}} }\\
+&=\bigoplus_{k=0}^n \left( \bigoplus_{i=n'_k}^{n'_{k+1}-1}\vis{\beta_{ij}^{j\in J\cap \Holes(Q)}\subst{\bigodot_{j=i-1}^{n'_k}\!\!\Post''_{j}\bigodot_{j=n'_k-1}^{0}\!\!\Post''_{j}}}\right)\\
+&=\bigoplus_{k=0}^n \left( \gamma_{kj}^{j\in J\cap \Holes(Q)}\subst{\bigodot_{j=k-1}^{0}\!\!\Post_{k}}\right)
 \end{split}\end{equation*}
@@
 %%and similarly for $\beta_p$. Thus, we can rewrite $\gamma$ given in the hypothesis as: \\
-%%$\set{\gamma}= \displaystyle{\mybigdotcup_{p=0}^{n}
+%%$\set{\gamma}= \displaystyle{\bigoplus_{p=0}^{n}
 %%\vis{\set{\beta_{p}}}\subst{\bigodot_{p=n}^{0} \Post_{p}}}$\\
@@
 $\Pred\,'=\Pred\land (\beta_{j_0}=\alpha_Q\land \Pred_Q) \quad\text{~~and~~}\quad
-%\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
+%\forall j\in J_t,\,\gamma_j= \displaystyle{\bigoplus_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
 \Post\,'=\Post\uplus\Post_Q
@@
 \begin{align*}
-\set{\gamma}=&\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\!\!\bigodot_{j=h-1}^{0}\!\! \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigodot_{j=k}^{0}\!\!\Post_{1j}}} \dotcup\\&
+\set{\gamma}=&\bigoplus_{h=0}^k \vis{\set{\beta_{1h}}\subst{\!\!\bigodot_{j=h-1}^{0}\!\! \Post_{1j} } }  \oplus  \vis{\set{\beta_2}\subst{\bigodot_{j=k}^{0}\!\!\Post_{1j}}} \oplus\\&
 		%&
- \mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\!\!\bigodot_{j=h-1}^{0}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=k}^{0}\Post_{1j}} }\\
+ \bigoplus_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\!\!\bigodot_{j=h-1}^{0}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=k}^{0}\Post_{1j}} }\\
 \Pred_Q=&\bigwedge_{h=0}^{k}\!\Pred_{1h}\subst{\!\!\bigodot_{j=h-1}^{0}\!\!\!\!\Post_{1 j}}\land \Pred_2\subst{\bigodot_{h=k}^{0}\Post_{1h}}\land\\
@@
 \begin{align*}
-\set{\gamma_c}=&\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigodot_{i=h-1}^{0}\!\!
-\Post_{1i} } }  \dotcup  \vis{({\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2})\subst{\bigodot_{i=k}^{0}\Post_{1i}}} \dotcup\\
-&\mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigodot_{i=h-1}^{0}\!\!\Post_{3i}\shortodot\Post_2\shortodot\bigodot_{i=k}^{0}\Post_{1i}} }\\
+\set{\gamma_c}=&\bigoplus_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigodot_{i=h-1}^{0}\!\!
+\Post_{1i} } }  \oplus  \vis{({\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2})\subst{\bigodot_{i=k}^{0}\Post_{1i}}} \oplus\\
+&\bigoplus_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigodot_{i=h-1}^{0}\!\!\Post_{3i}\shortodot\Post_2\shortodot\bigodot_{i=k}^{0}\Post_{1i}} }\\
 =&\set{\gamma}\uplus\vis{\beta_j^{\in J\setminus \{j_0\}}} \quad  \text{ because $\Post_{1j}$  does not act on variables of $\beta_j$.}  
@@
 
-\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}\subst{\bigodot_{k=p}^{0}{\Post_k}}}
+\forall j\in J_p,\,\gamma_j= \displaystyle{\bigoplus_{p=0}^n \gamma_{p j}\subst{\bigodot_{k=p}^{0}{\Post_k}}}
 
@@
 \alpha=&\alpha'{\subst{\bigodot_{j=m_1}^{0}\Post_{1j}}} \\
-\gamma_j^{j\in J}=&{\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigodot_{k=i-1}^{0}\!\!
-\Post_{1k} } }  \dotcup \, \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigodot_{k=m_1}^{0}\Post_{1k}}}}\, \dotcup\\
-&\mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{3p}} \subst{\bigodot_{k=i-1}^{0}\Post_{3k}\shortodot\Post_2\shortodot\bigodot_{k=m_1}^{0}\Post_{1k}}}\\
+\gamma_j^{j\in J}=&{\bigoplus_{i=0}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigodot_{k=i-1}^{0}\!\!
+\Post_{1k} } }  \oplus \, \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigodot_{k=m_1}^{0}\Post_{1k}}}}\, \oplus\\
+&\bigoplus_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{3p}} \subst{\bigodot_{k=i-1}^{0}\Post_{3k}\shortodot\Post_2\shortodot\bigodot_{k=m_1}^{0}\Post_{1k}}}\\
 \Pred=&{\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\subst{\!\bigodot_{j=p-1}^{0}\!\!\Post_{1j}}\big)\land\Pred_2\subst{\!\bigodot_{p=m_1}^{0}\!\!\Post_{1p}}\land}\\ 
@@
  =&\!\!
-{\mybigdotcup_{\substack{i=0\\j_0\in J_{1i}}}^{m_1}\!\!\!
-\vis{{\beta_{1ij_0}}\subst{\!\bigodot_{k=i-1}^{0} \!\!\!\!\Post_{1k} } }  \,\dotcup\, \vis{{\beta_{2j_0}}\subst{\!\bigodot_{k=m_1}^{0}\!\!\!\Post_{1k}}}}\dotcup\!
+{\bigoplus_{\substack{i=0\\j_0\in J_{1i}}}^{m_1}\!\!\!
+\vis{{\beta_{1ij_0}}\subst{\!\bigodot_{k=i-1}^{0} \!\!\!\!\Post_{1k} } }  \,\oplus\, \vis{{\beta_{2j_0}}\subst{\!\bigodot_{k=m_1}^{0}\!\!\!\Post_{1k}}}}\oplus\!
 \\
 &\qquad\qquad
-{ \!\mybigdotcup_{\substack{i=0\\j_0\in J_{3i}}}^{m_2}\!\! \vis{{\beta_{3ij_0}} \subst{\!\bigodot_{k=i-1}^{0}\!\!\!\Post_{3k}\shortodot\Post_2\shortodot
+{ \!\bigoplus_{\substack{i=0\\j_0\in J_{3i}}}^{m_2}\!\! \vis{{\beta_{3ij_0}} \subst{\!\bigodot_{k=i-1}^{0}\!\!\!\Post_{3k}\shortodot\Post_2\shortodot
 \!\!\bigodot_{k=m_1}^{0}\!\!\!\Post_{1k}}}}
@@
 \set{\gamma'}=&
- \mybigdotcup_{i=0}^{m_1}\set{\gamma'_{1i}}\subst{\bigodot_{k=i-1}^{0}\Post\,'_{1k}}\,\dotcup\,
-\set{\gamma'_{2}}\subst{\bigodot_{k=m_1}^{0}\Post\,'_{1k}}\,\dotcup\\&\qquad
- \mybigdotcup_{i=0}^{m_2}\set{\gamma'_{3i}}\subst{\bigodot_{k=i-1}^{0}\Post\,'_{3k}\shortodot\Post\,'_2\shortodot\bigodot_{k=n}^{0}\Post\,'_{1k}}
+ \bigoplus_{i=0}^{m_1}\set{\gamma'_{1i}}\subst{\bigodot_{k=i-1}^{0}\Post\,'_{1k}}\,\oplus\,
+\set{\gamma'_{2}}\subst{\bigodot_{k=m_1}^{0}\Post\,'_{1k}}\,\oplus\\&\qquad
+ \bigoplus_{i=0}^{m_2}\set{\gamma'_{3i}}\subst{\bigodot_{k=i-1}^{0}\Post\,'_{3k}\shortodot\Post\,'_2\shortodot\bigodot_{k=n}^{0}\Post\,'_{1k}}
 \displaybreak[0]\\
@@
 {\small \begin{equation*}
-\begin{split}\gamma'_j=&\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}}\subst{\bigodot_{k=i-1}^{0}\! \Post_{1k} } }  \dotcup  \vis{{\beta_{2j}}\subst{\bigodot_{k=m_1}^{0}\!\Post_{1k}}}\, \dotcup\\&
-\mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij} \subst{\!\bigodot_{k=i-1}^{0}\!\!\!\Post_{3k}\shortodot\Post_2\shortodot\bigodot_{k=m_1}^{0}\!\!\Post_{1k}}}
+\begin{split}\gamma'_j=&\bigoplus_{i=0}^{m_1} \vis{{\beta_{1ij}}\subst{\bigodot_{k=i-1}^{0}\! \Post_{1k} } }  \oplus  \vis{{\beta_{2j}}\subst{\bigodot_{k=m_1}^{0}\!\Post_{1k}}}\, \oplus\\&
+\bigoplus_{i=0}^{m_2} \vis{\beta_{3ij} \subst{\!\bigodot_{k=i-1}^{0}\!\!\!\Post_{3k}\shortodot\Post_2\shortodot\bigodot_{k=m_1}^{0}\!\!\Post_{1k}}}
 \end{split}
@@
 \gamma'_j =&
-\mybigdotcup_{i=0}^{m_1}{\gamma'_{1ij}}\subst{\bigodot_{k=i-1}^{0}\Post\,'_{1k}}\dotcup
- {\gamma'_{2 j}}\subst{\bigodot_{k=m_1}^{0}\Post\,'_{1k}}\,\dotcup\\&\quad \mybigdotcup_{i=0}^{m_2}{\gamma'_{3ij}}\subst{\bigodot_{k=i-1}^{0}\Post\,'_{3k}\shortodot\Post\,'_2\shortodot\bigodot_{k=n}^{0}\Post\,'_{1k}}\\
+\bigoplus_{i=0}^{m_1}{\gamma'_{1ij}}\subst{\bigodot_{k=i-1}^{0}\Post\,'_{1k}}\oplus
+ {\gamma'_{2 j}}\subst{\bigodot_{k=m_1}^{0}\Post\,'_{1k}}\,\oplus\\&\quad \bigoplus_{i=0}^{m_2}{\gamma'_{3ij}}\subst{\bigodot_{k=i-1}^{0}\Post\,'_{3k}\shortodot\Post\,'_2\shortodot\bigodot_{k=n}^{0}\Post\,'_{1k}}\\
 =&
-{\mybigdotcup_{t=0}^{n} {\gamma_{tj}}\subst{\bigodot_{k=t-1}^{0} \Post_{k}}}   
+{\bigoplus_{t=0}^{n} {\gamma_{tj}}\subst{\bigodot_{k=t-1}^{0} \Post_{k}}}   
 \end{split}

### 2022-10-18 2016-Weak-FH-Bisim/WeakBisim.tex
version without symbol change
passe eric+Rabea

@@
 }
-\TODO{Rabea: look for papers by Larsen end Liu on context systems, and Larsen and Huttel on static constructs}
+%\TODO{Rabea: look for papers by Larsen end Liu on context systems, and Larsen and Huttel on static constructs}
 
@@
 We first define (in Definition~\ref{def:Non-ObsTau}) systems that cannot observe $\tau$ actions of sub-systems; namely pNets that cannot change their state, or emit an observable action when one of its holes emits a $\tau$ action.
-\TODO{Eric: discuss rel with Vaandrager - ou pas !!}
+%\TODO{Eric: discuss rel with Vaandrager - ou pas !!}
 
@@
 
-Thus, we let $\gamma$ range over sequences of action terms and use $\dotcup$ as the concatenation operator that appends sequences of action terms: given two sequences of action terms  $\gamma\oplus\gamma'$ concatenates the two sequences.
+Thus, we let $\gamma$ range over sequences of action terms and use $\oplus$ as the concatenation operator that appends sequences of action terms: given two sequences of action terms  $\gamma\oplus\gamma'$ concatenates the two sequences.
 The operation is lifted to indexed sets of sequences:   at each index $i$, $\set {\gamma_1}\oplus \set {\gamma_2}$ concatenates the sequences of actions at index $i$ of $\set{\gamma_1}$ and the one at index $i$ of $\set {\gamma_2}$\footnote{One of the two sequences is empty when $i\not \in \dom(\set{\gamma_1})$ or $i\not \in \dom(\set{\gamma_2})$ .}.
@@
 \\
-\set{\gamma}=\set{\gamma_1}\dotcup \set{\gamma_2}\subst{\Post_1}\oplus\set{\gamma_3}\subst{\Post_2\shortodot \Post_1}\\
+\set{\gamma}=\set{\gamma_1}\oplus \set{\gamma_2}\subst{\Post_1}\oplus\set{\gamma_3}\subst{\Post_2\shortodot \Post_1}\\
 \alpha'=\alpha\subst{\Post_1}\\
@@
 \alpha=&\alpha'{\subst{\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}}\\
-\gamma_j^{j\in J}=&\mybigoplus_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{0}\!\! \Post_{1j}}}\oplus\\&  \vis{\set{\beta_2}\subst{\bigodot_{j=m_1}^{0}\Post_{1j}}} \oplus  
+\gamma_j^{j\in J}=&\bigoplus_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{0}\!\! \Post_{1j}}}\oplus\\&  \vis{\set{\beta_2}\subst{\bigodot_{j=m_1}^{0}\Post_{1j}}} \oplus  
 {\bigoplus_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}} }}

### 2022-10-19 2016-Weak-FH-Bisim/WeakBisim.tex
ajout ref huttel
mucrl2

--- 2022-10-18 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 cases where the original transition can be triggered. %\TODO{Eric: is this like in symbolic bisimulation ?}
-\ERIC{This is similar to the early and late symbolic bisimulation equivalences for value-passing CCS \cite{HENNESSY:1995}, though we use more general definitions in our setting.}
+\ERIC{This is similar to the early and late symbolic bisimulation equivalences for value-passing CCS \cite{HENNESSY:1995}, though we need more general definitions in our setting.}
 
 Compositionality of bisimilarity in our model comes from the specification of the interactions, including actions of the holes. 
-\ERIC{This is quite different from the works on contextual equivalences, e.g. \cite{Larsen87, Larsen:91}; we will give more details on this in section \ref{sec:RW}.}
+\ERIC{This is quite different from the works on contextual equivalences, e.g. \cite{Larsen:91}; we will give more details on this in section \ref{sec:RW}.}
 In pNets, synchronisation vectors define the possible interactions between the pNet that fills the hole and the surrounding pNets.
@@
 This approach also allows us to specify a sufficient condition on allowed transitions to make weak bisimilarity compositional; namely it is not possible to synchronise on invisible actions from the holes or prevent them to occur.
-\ERIC{This is loosely related to works on the syntactic conditions on SOS rules to check whether weak bisimulation is a congruence for some process algebra operators \cite{GrootVaandrager1992}.
-Our approach is semantical and more global: our sufficient condition applies to a whole (open) system, and is expressed on its open automaton (see Definition \ref{def:non-obspNet}).}
-%\TODO{Eric: relations with SOS rule formats?}
+\TODO{Eric: relations with SOS rule formats?}
 
@@
 We also adopt a semantics and logical interpretation of the automata that intuitively can be stated as follows: ``if a transition belongs to an open automaton, any refinement of this transition also belongs to the automaton''.
-\LUDO{Our open automata are clearly inspired by the work  of De Simone on formatting of SOS rules~\cite{deSimone85}.
+\LUDO{Our open automata are clearly inspired by the work  of de Simone on formatting of SOS rules~\cite{deSimone85}.
 A precise comparison with related works can be found in Section~\ref{sec:RW}.}
@@
  that pioneered this idea.
-\ERIC{Indeed, our definition uses both hypotheses on the behaviour of holes, as in \cite{deSimone85}, and symbolic manipulation of action expressions, as in symbolic bisimulations of \cite{HENNESSY:1995}.
-}
-%\TODO{Eric: combination of RdS, symb bisim, and more}
+\TODO{Eric: combination of RdS, symb bisim, and more}
 
@@
 \begin{thm}[Congruence]\label{thm-congr-eq}
-	Consider an open pNet \\
+	Consider an open pNet:
 	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
@@
 Defining properly the interaction between a logical formulae in the action and the logics of the pNet composition seems very difficult.
-mCRL2~\cite{} is another effective model for specifying and proving properties of concurrent systems.
+mCRL2~\cite{mCRLFACS:2020} is another effective model for specifying and proving properties of concurrent systems.
 mCRL2 has an established tool-suite and share similarities with pNets.
@@
 
-Quotienting of process algebras~\cite{Larsen:91} and decomposition techniques for MCRL2~\cite{LaveauxWillemse:ICE21} share similarities with our approach; they propose to 
+Quotienting of process algebras~\cite{Larsen:91} and decomposition techniques for mCRL2~\cite{LaveauxWillemse:ICE21} share similarities with our approach; they propose to 
 overcome the state-space-explosion problem by decomposing formulas to be verified according to the process composition. The decomposed problem must be equivalent to the original one.
@@
 There is also a clear relation with the seminal works on rule formats for Structured Operational Semantics, e.g.
-De Simone format, GSOS, and conditional rules with or without negative premises \cite{deSimone85,Bloom:1995,GROOTE1992202,VANGLABBEEK2004229}.
+DeSimone format, GSOS, and conditional rules with or without negative premises \cite{deSimone85,Bloom:1995,GROOTE1992202,VANGLABBEEK2004229}.
 The Open pNets model provides a way to define operators similar to these rules formats, but with quite different aim and approach.

### 2022-10-19 2016-Weak-FH-Bisim/WeakBisim.tex

--- 2022-10-18 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 }
+
+\RAB{
+PNets have features of "known" compositional specification theory  allowing for modular and possibly incomplete  description   and  structural compositions \cite{HuttelL89,Larsen:91} of systems.}
+
 %\TODO{Rabea: look for papers by Larsen end Liu on context systems, and Larsen and Huttel on static constructs}

### 2022-10-19 2016-Weak-FH-Bisim/WeakBisim.tex
RW organisation

@@
 
-\ERIC{Beware that even if open transitions may look similar to the notion of Transition System Specification \cite{GROOTE1992202,GROOTE20063} and other forms of SOS rules, they are \emph{not} structural rules, but rules defining the behaviour of the global states of the system.
-}
+Beware that even if open transitions may look similar to the notion of Transition System Specification \cite{GROOTE1992202,GROOTE20063} and other forms of SOS rules, they are \emph{not} structural rules, but rules defining the behaviour of the global states of the system.
 
@@
 This approach also allows us to specify a sufficient condition on allowed transitions to make weak bisimilarity compositional; namely it is not possible to synchronise on invisible actions from the holes or prevent them to occur.
-\ERIC{This is loosely related to works on the syntactic conditions on SOS rules to check whether weak bisimulation is a congruence for some process algebra operators \cite{GrootVaandrager1992}.
-Our approach is semantical and more global: our sufficient condition applies to a whole (open) system, and is expressed on its open automaton (see Definition \ref{def:non-obspNet}).}
+This is loosely related to works on the syntactic conditions on SOS rules to check whether weak bisimulation is a congruence for some process algebra operators \cite{GrootVaandrager1992}.
+Our approach is semantical and more global: our sufficient condition applies to all the synchronisations at a given composition level of an (open) system and not on individual rules.
+It is expressed on the open automaton (see Definition \ref{def:non-obspNet}).
 %\TODO{Eric: relations with SOS rule formats?}
@@
 
-\RAB{In the same vein as for context systems \cite{Larsen:91}, pNets is a formalism for modular and possibly incomplete  description of concurrent systems.
-The two formalisms are however different as the theory of contexts relies on a form of rewrite rules, while  pNets rely on parametric automata to express the system behaviour.
-}
-
-\RAB{
-PNets have features of "known" compositional specification theory  allowing for modular and possibly incomplete  description   and  structural compositions \cite{HuttelL89,Larsen:91} of systems.}
-
 %\TODO{Rabea: look for papers by Larsen end Liu on context systems, and Larsen and Huttel on static constructs}
@@
 
+In the same vein as  context systems \cite{Larsen:91}, pNets is a formalism for modular and possibly incomplete  description of concurrent systems.
+The two formalisms are however different as the theory of contexts relies on a form of rewrite rules, while  pNets rely on parametric automata to express the system behaviour.
+PNets have similar features as context systems \cite{Larsen:91} and static constructs \cite{HuttelL89}.
+Indeed all these approaches allow for modular and possibly incomplete  description   and  structural composition of systems.
+The main originality of pNets  compared to these other compositional approaches is the parameterised nature of the specification, which enables reasoning on value-passing systems but also on rich synchronisations that depend on the value of parameters.
+
+\subsubsection*{Decomposition techniques}
+
 Quotienting of process algebras~\cite{Larsen:91} and decomposition techniques for mCRL2~\cite{LaveauxWillemse:ICE21} share similarities with our approach; they propose to 
@@
 Both parallel composition~\cite{Larsen:91} and mCRL2~\cite{LaveauxWillemse:ICE21} feature a concrete verification setting where decomposition is useful, while open automata provide a more general setting that could be used to represent both frameworks and hopefully generalise process decomposition results of \cite{Larsen:91,LaveauxWillemse:ICE21}.
+
+\subsubsection*{Logical and semantics approaches}
 

### 2022-10-19 2016-Weak-FH-Bisim/WeakBisim.tex
letter and blue

@@
 cases where the original transition can be triggered. %\TODO{Eric: is this like in symbolic bisimulation ?}
-\ERIC{This is similar to the early and late symbolic bisimulation equivalences for value-passing CCS \cite{HENNESSY:1995}, though we use more general definitions in our setting.}
+This is similar to the early and late symbolic bisimulation equivalences for value-passing CCS \cite{HENNESSY:1995}, though we use more general definitions in our setting.
 
 Compositionality of bisimilarity in our model comes from the specification of the interactions, including actions of the holes. 
-\ERIC{This is quite different from the works on contextual equivalences, e.g. \cite{Larsen87, Larsen:91}; we will give more details on this in section \ref{sec:RW}.}
+This is quite different from the works on contextual equivalences, e.g. \cite{Larsen87, Larsen:91}; we will provide a detailed comparison in Section~\ref{sec:RW}.
 In pNets, synchronisation vectors define the possible interactions between the pNet that fills the hole and the surrounding pNets.
@@
 We also adopt a semantics and logical interpretation of the automata that intuitively can be stated as follows: ``if a transition belongs to an open automaton, any refinement of this transition also belongs to the automaton''.
-\LUDO{Our open automata are clearly inspired by the work  of De Simone on formatting of SOS rules~\cite{deSimone85}.
+{Our open automata are clearly inspired by the work  of De Simone on formatting of SOS rules~\cite{deSimone85}.
 A precise comparison with related works can be found in Section~\ref{sec:RW}.}
@@
  that pioneered this idea.
-\ERIC{Indeed, our definition uses both hypotheses on the behaviour of holes, as in \cite{deSimone85}, and symbolic manipulation of action expressions, as in symbolic bisimulations of \cite{HENNESSY:1995}.
-}
+Indeed, our definition uses both hypotheses on the behaviour of holes, as in \cite{deSimone85}, and symbolic manipulation of action expressions, as in symbolic bisimulations of \cite{HENNESSY:1995}. 
 %\TODO{Eric: combination of RdS, symb bisim, and more}
@@
           {s_1 \OTarrow {\alpha(x)} s_1'}\]
-Bisimulation should allow it to be matched by the two following ones (depending on the value of $x$), to prove the bisimulation $\mathcal{R}=\{(s_1,s_2,\True),(s_1',s_2',\True)\}$
+Bisimulation should allow it to be matched by the two following ones (depending on the value of $x$), to prove that the relation $\mathcal{R}=\{(s_1,s_2,\True),(s_1',s_2',\True)\}$ is a bisimulation.
 \[ \openrule
@@
 The two formalisms are however different as the theory of contexts relies on a form of rewrite rules, while  pNets rely on parametric automata to express the system behaviour.
-PNets have similar features as context systems \cite{Larsen:91} and static constructs \cite{HuttelL89}.
+pNets have similar features as context systems \cite{Larsen:91} and static constructs \cite{HuttelL89}.
 Indeed all these approaches allow for modular and possibly incomplete  description   and  structural composition of systems.
@@
 
-\LUDO{
-pNets support the refinement checking at the automaton level through a simulation approach, with symbolic evaluation of
-the guards and transitions. 
+The pNets formalism supports the refinement checking at the automaton level through a simulation, with symbolic evaluation of
+ guards and transitions. 
  The definition of simulation on open automata should be  stronger than a classical simulation since it matches a transition with a family of transitions.
@@
 A useful simulation relation  should thus support the  comparison of automata that do not have the same number of holes.
-Designing such a simulation relation is a non-trivial extension that we leave for future work.}
+Designing such a simulation relation is a non-trivial extension that we leave for future work.
 

### 2022-10-19 2016-Weak-FH-Bisim/WeakBisim.tex
abs

@@
 
-Establishing equivalences between programs or systems is crucial both for verifying correctness of programs and for justifying optimisations and program transformations.
+Establishing equivalences between programs  is crucial both for verifying correctness of programs and for justifying optimisations and program transformations.
 There exist several equivalence relations for programs, and bisimulations are among the most versatile of these equivalences.
 Among bisimulations one distinguishes strong bisimulation that requires that each action of a program is simulated by a single action of the equivalent program, and weak bisimulation that  allows some of the actions to be
-  invisible, and thus not simulated by the equivalent program.
+  invisible, and thus not simulated.
 
@@
 Open pNets are pNets with holes, i.e.
-placeholders inside the hierarchical structure  that can be filled later by sub-systems.
+placeholders   that can be filled later by sub-systems.
 However, there is no standard tool for defining the semantics of an open system in this context.
@@
   the classical \emph{weak bisimulation} equivalence, and study its properties.
-Among these properties we are interested in compositionality: if two systems are proven equivalent they will be undistinguishable by their context, and they will also be indistinguishable when their holes are filled with equivalent systems.
+Among these properties we are interested in compositionality: if two systems are proven equivalent they will be indistinguishable by their context, and they will also be indistinguishable when their holes are filled with equivalent systems.
 We identify sufficient conditions to ensure compositionality of strong and weak bisimulation.

### 2022-10-19 2016-Weak-FH-Bisim/WeakBisim.tex
minor

@@
 The simulation of one transition by many others is one non-standard aspect of this definition. This is made necessary by the parameterised nature of our model. Consider the following open transition.
-\[ \openrule
-         {
-           \set{\beta}, \True,\subst{y\leftarrow x}}
+\[ \openrule         {  \set{\beta}, \True,\subst{y\leftarrow x}}
           {s_1 \OTarrow {\alpha(x)} s_1'}\]

### 2022-10-19 2016-Weak-FH-Bisim/WeakBisim.tex
diff
fig

@@
 The simulation of one transition by many others is one non-standard aspect of this definition. This is made necessary by the parameterised nature of our model. Consider the following open transition.
-\[ \openrule         {  \set{\beta}, \True,\subst{y\leftarrow x}}
+\[ \openrule
+		{  \set{\beta}, \True,\subst{y\leftarrow x}}
           {s_1 \OTarrow {\alpha(x)} s_1'}\]
@@
 This is done in a way that resembles the process of $\tau$ saturation: we add  $\tau$ open transitions before or after another open transition, regardless of whether it is observable or not.
-\begin{definition}[Building a weak open automaton]\label{def:buildweakOT}~\\
-  Let $A = \mylangle J,\mathcal{S},s_0,V,\mathcal{T}\myrangle$ be an open automaton. 
-The weak open automaton \emph{derived} from $A$ is an open automaton  $\mylangle J,\mathcal{S},s_0,V,\WT\myrangle$ where $\WT$ is derived from $\mathcal{T}$ by saturation, applying the rules of Figure~\ref{fig:WT}:
-%\noindent{\bf Invisible $\tau$ transitions:}
+
 \begin{figure}[tb]
@@
 \end{figure}
+\begin{definition}[Building a weak open automaton]\label{def:buildweakOT}~\\
+  Let $A = \mylangle J,\mathcal{S},s_0,V,\mathcal{T}\myrangle$ be an open automaton. 
+The weak open automaton \emph{derived} from $A$ is an open automaton  $\mylangle J,\mathcal{S},s_0,V,\WT\myrangle$ where $\WT$ is derived from $\mathcal{T}$ by saturation, applying the rules of Figure~\ref{fig:WT}.
 \end{definition}

### 2022-10-19 2016-Weak-FH-Bisim/WeakBisim.tex
resolution pbme doublons refs

@@
 This approach also allows us to specify a sufficient condition on allowed transitions to make weak bisimilarity compositional; namely it is not possible to synchronise on invisible actions from the holes or prevent them to occur.
-This is loosely related to works on the syntactic conditions on SOS rules to check whether weak bisimulation is a congruence for some process algebra operators \cite{GrootVaandrager1992}.
+This is loosely related to works on the syntactic conditions on SOS rules to check whether weak bisimulation is a congruence for some process algebra operators \cite{GROOTE1992202}.
 Our approach is semantical and more global: our sufficient condition applies to all the synchronisations at a given composition level of an (open) system and not on individual rules.

### 2022-10-19 2016-Weak-FH-Bisim/JLAMP-AnswerToReviewers.tex
letter and blue
debut de la lettre

@@
 \usepackage{color}
+\newenvironment{review}{\bgroup\itshape\begin{quote}}{\end{quote}\egroup}
+
 \newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
@@
 
+Please find enclosed the revision of our submission to JLAMP. We improved our article according to the comments made by the
+anonymous reviewers.
+
+We would first like to thank the reviewers for their analysis of our
+paper, and for their insightful comments and advices that extremely strengthen the quality of our paper.
+%and the useful advices they gave us.
+
+We detail below the major changes we made in this revision and explain how we addressed them.  \emph{Comments that are  addressed trivially and exactly as suggested by the reviewers are omitted}.
+
+\medskip
+
+%After this, we will review in the next pages the comments of the reviewers and explain how we addressed them.
+
+\section*{Response to reviewer 1}
+
+\begin{review}
+blabla de la review
+\end{review}
+Answer
+
+\begin{review}
+suite
+\end{review}
+bla
+
+\newpage
+
+As explained above, we quote below and reply to text requiring changes that we did not  address in a straightforward manner.
+We additionally produced a version of the paper highlighting all the changes we made: \TODO{Si tu arrives a produire le latexdiff} \url{url???}
+
 \ERIC{P4, *say that this is like in Symbolic Bisimulation}
@@
 \ERIC{P4, *Any relations with the conditions on SOS rule formats guaranteeing compositionality of weak bisimilarity?}
-\begin{quote} non je n'ai pas repondu ici... voir paragraph page precedente, est-ce suffisant "
+\begin{quote} 
+\TODO{L'ajout est dans l'introduction pargra. avant la structure}
+non je n'ai pas repondu ici... voir paragraph page precedente, est-ce suffisant "
 \end{quote}
 
-\ERIC{P14, *Is your definition a combination of De Simone FH-bisimulation and Hennessy and Lin's symbolic bisimulation?
+\ERIC{P14, *Is your definition a combination of De Simone FH-bisimulation and Hennessy and Lin's symbolic bisimulation?}
 \begin{quote}
+\TODO{L'ajout est dans la section 3.2, fin pargraph 1}
 Je n'ai pas redige ca... mais l'idee pourrait etre que en gros oui, et en y ajoutant le formalisme synch vecteurs de Arnold et Nivat, 
@@
 \begin{quote}
+\TODO{L'ajout est dans la conclusion [30,31]...}
+
 J'ai ajoute 7 ligns ici: "In this platform [...] different encodings of operators".

### 2022-10-19 2016-Weak-FH-Bisim/WeakBisim.tex
correction mineure

@@
 The semantics of pNets can be expressed as a translation to a labelled transition system (LTS), but only if the pNet has no parameter and no hole.
-Adding parameters to a LTS is quite standard \ERIC{\cite{Lin:96}} but enabling holes inside LTSs is not a standard notion.
+Adding parameters to a LTS is quite standard \cite{Lin:96} but enabling holes inside LTSs is not a standard notion.
 
@@
 These are however technically more complex than the ones for open automata because each hole performs a set of actions, and thus a composed transition is the composition of one transition of the top-level pNet and a sequence of transitions of the sub-pNet that fills its hole.
-Composition and decomposition properties can be found as Lemmas~\ref{lem-decomposeWOT}, Lemma~\ref{lem-Weakcompose1}, and Lemma~\ref{lem-Weakcompose} in~\ref{sec:app-composition}.
+Composition and decomposition properties can be found as Lemma~\ref{lem-decomposeWOT}, Lemma~\ref{lem-Weakcompose1}, and Lemma~\ref{lem-Weakcompose} in~\ref{sec:app-composition}.
 

### 2022-10-19 2016-Weak-FH-Bisim/WeakBisim.tex
played with indices

--- 2022-10-19 2016-Weak-FH-Bisim/WeakBisim.tex
@@
 We  define a quantified composition operator for effects, i.e. $\Post$ elements of the open transitions.
-We use ${\displaystyle \bigodot_{i=n}^{0} \Post_i}$ to denote  $\Post_n\otimes .. \otimes \Post_0$. By convention ${\displaystyle \bigodot_{i=-1}^{0} \Post_i}$ is the identity.
+We use ${\displaystyle \bigodot_{i=n}^{1} \Post_i}$ to denote  $\Post_n\otimes .. \otimes \Post_0$. By convention ${\displaystyle \bigodot_{i=0}^{1} \Post_i}$ is the identity.
 
@@
 \alpha = \tau \wedge  \set{\gamma}=\emptyset \wedge \Pred =\True \wedge \Post =\Id(s)\wedge s=s'$; or \\ 
-there exist   $\set{\beta_{1i}}$, $\set{\beta_{2i}}$, and $\set{\beta_{3i}}$, $\Pred_{1i}$, $\Pred_{3i}$, $\Post_{1i}$, and  $\Pred_2$, $\Post_2$, $n\geq -1$, $m\geq -1$ s.t.\footnote{$n=-1$ (resp.
-$m=-1$) corresponds to the case where there is no $\tau$ transition before (resp.
+there exist   $\set{\beta_{1i}}$, $\set{\beta_{2i}}$, and $\set{\beta_{3i}}$, $\Pred_{1i}$, $\Pred_{3i}$, $\Post_{1i}$, and  $\Pred_2$, $\Post_2$, $n\geq 0$, $m\geq 0$ s.t.\footnote{$n=0$ (resp.
+$m=0$) corresponds to the case where there is no $\tau$ transition before (resp.
 after) the transition $\alpha$.}:
@@
 $
-\alpha'=\alpha\displaystyle{\subst{\bigodot_{j=n}^{0}\Post_{1j}}}\\
-s=s_{10} \wedge s_{1(n+1)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
+\alpha'=\alpha\displaystyle{\subst{\bigodot_{j=n}^{1}\Post_{1j}}}\\
+s=s_{11} \wedge s_{1(n+1)}=s_2 \wedge s'_2 = s_{31} \wedge s_{3(m+1)}=s'\\
 \displaystyle{
-\set{\gamma}=\bigoplus_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{0} \Post_{1j} } }  \oplus  \vis{\set{\beta_2}\subst{\bigodot_{j=n}^{0}\Post_{1j}}} \oplus}\\
-{}~\qquad \displaystyle{\bigoplus_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}} }}
+\set{\gamma}=\bigoplus_{i=1}^n \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{1} \Post_{1j} } }  \oplus  \vis{\set{\beta_2}\subst{\bigodot_{j=n}^{1}\Post_{1j}}} \oplus}\\
+{}~\qquad \displaystyle{\bigoplus_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{1}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{1}\Post_{1j}} }}
 \\
-\Pred=\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigodot_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j=n}^{0}\Post_{1j}}\land\\ 
-{}~\qquad\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}}\Big)\\
-\Post=\bigodot_{j=m}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}
+\Pred=\bigwedge_{i=1}^n\Pred_{1i}\subst{\bigodot_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j=n}^{1}\Post_{1j}}\land\\ 
+{}~\qquad\quad\Big(\bigwedge_{i=1}^m\Pred_{3i}\subst{\bigodot_{j=i-1}^{1}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{1}\Post_{1j}}\Big)\\
+\Post=\bigodot_{j=m}^{1}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{1}\Post_{1j}
 $
@@
 \begin{proof}
- ($\Rightarrow$) We present an induction on $n$ and $m$, focusing on the incrementation on $n$: we prove that the property is valid for $m=-1$, $n=-1$ apply a first induction proof for going from $n$ to $n+1$, a similar induction can be applied to go from $m$ to $m+1$ (omitted).
+ ($\Rightarrow$) We present an induction on $n$ and $m$, focusing on the incrementation on $n$: we prove that the property is valid for $m=0$, $n=0$ apply a first induction proof for going from $n$ to $n+1$, a similar induction can be applied to go from $m$ to $m+1$ (omitted).
 \begin{itemize}
-\item The base case there is one transition, so $n=-1$ and $m=-1$, we have:
+\item The base case there is one transition, so $n=0$ and $m=0$, we have:
 \begin{mathpar}
@@
 We want to prove (1) $\Rightarrow$ (2) in the lemma, and in (1) we  focus on the case where there is a set of open transitions (this is the case: $s\neq s'$).
-In other words, we consider the sequence of ($n+m+4$) open transitions:
-\begin{mathpar}
-\Big(\forall i \in [0..n+1].\openrule
+In other words, we consider the sequence of ($n+m+2$) open transitions:
+\begin{mathpar}
+\Big(\forall i \in [1..n+1].\openrule
     {
@@
 \, \wedge\\
-{}~~\hspace{2.25cm}\forall i \in [0..m].\openrule
+{}~~\hspace{2.25cm}\forall i \in [1..m].\openrule
          {
@@
 \begin{align*}
-s''=s_{10} &\wedge s_{1(n+2)}=s_2 \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
-\alpha'=&\alpha\displaystyle{\subst{\bigodot_{j=n+1}^{1}\!\!\Post_{1j}}}\\
-\set{\gamma}=&\bigoplus_{i=1}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{1} \Post_{1j} } }  \oplus  \vis{\set{\beta_2}\subst{\bigodot_{j=n+1}^{1}\Post_{1j}}} \oplus\\
-& \bigoplus_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}} }\\
-\Pred=&\bigwedge_{i=1}^{n+1}\Pred_{1i}\subst{\bigodot_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j={n+1}}^{1}\Post_{1j}}\land\\ 
-&\quad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j={n+1}}^{1}\Post_{1j}}\Big)\\
-\Post=&\bigodot_{j=m}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j={n+1}}^{1}\Post_{1j}
+s''=s_{12} &\wedge s_{1(n+2)}=s_2 \wedge s'_2 = s_{31} \wedge s_{3(m+1)}=s'\\
+\alpha'=&\alpha\displaystyle{\subst{\bigodot_{j=n+1}^{2}\!\!\Post_{1j}}}\\
+\set{\gamma}=&\bigoplus_{i=2}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{2} \Post_{1j} } }  \oplus  \vis{\set{\beta_2}\subst{\bigodot_{j=n+1}^{2}\Post_{1j}}} \oplus\\
+& \bigoplus_{i=1}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{1}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{1}\Post_{1j}} }\\
+\Pred=&\bigwedge_{i=2}^{n+1}\Pred_{1i}\subst{\bigodot_{j=i-1}^{2}\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j={n+1}}^{2}\Post_{1j}}\land\\ 
+&\quad\Big(\bigwedge_{i=1}^m\Pred_{3i}\subst{\bigodot_{j=i-1}^{1}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j={n+1}}^{1}\Post_{1j}}\Big)\\
+\Post=&\bigodot_{j=m}^{1}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j={n+1}}^{2}\Post_{1j}
 \end{align*}
@@
        {
-           \vis{\set{\beta_{10}}}\!,\Pred_{10},\Post_{10}
-				 } {s_{10} \OTWeakarrow {\tau}s_{11}}\! \in\! \WT
+           \vis{\set{\beta_{11}}}\!,\Pred_{11},\Post_{1}
+				 } {s_{11} \OTWeakarrow {\tau}s_{12}}\! \in\! \WT
 \\
@@
 \\\\
-\set{\gamma''}= \vis{\set{\beta_{10}}} \oplus \set{\gamma}\subst{\Post_{10}}\\
-\Pred\,''\!=\!\Pred_{10}\land\Pred\subst{\Post_{10}}\\\\%\land (\Pred_3\subst{\Post_2})\subst{\Post_{10}}
-\Post\,''=\Id(s'')\shortodot\Post\shortodot\Post_{10} \\ \alpha''=\alpha'\subst{\Post_{10}}
+\set{\gamma''}= \vis{\set{\beta_{11}}} \oplus \set{\gamma}\subst{\Post_{1}}\\
+\Pred\,''\!=\!\Pred_{11}\land\Pred\subst{\Post_{11}}\\\\%\land (\Pred_3\subst{\Post_2})\subst{\Post_{11}}
+\Post\,''=\Id(s'')\shortodot\Post\shortodot\Post_{11} \\ \alpha''=\alpha'\subst{\Post_{11}}
 }
@@
 \begin{align*}
-s_{10}=s_{10} &\wedge s_{1(n+2)}=s_{2} \wedge s'_2 = s_{30} \wedge s_{3(m+1)}=s'\\
-\alpha''=&\alpha\subst{\bigodot_{j=n+1}^{1}\Post_{1j}}\subst{\Post_{10}} = \alpha\subst{\bigodot_{j=n+1}^{0}\Post_{1j}}\\
-\set{\gamma''}=&\bigoplus_{i=0}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{1} \Post_{1j} } }  \oplus  \vis{\set{\beta_2}\subst{\bigodot_{j=n+1}^{1}\Post_{1j}}} \oplus\\
-&\bigoplus_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}} }
+s_{11}=s_{11} &\wedge s_{1(n+2)}=s_{2} \wedge s'_2 = s_{31} \wedge s_{3(m+1)}=s'\\
+\alpha''=&\alpha\subst{\bigodot_{j=n+1}^{2}\Post_{1j}}\subst{\Post_{11}} = \alpha\subst{\bigodot_{j=n+1}^{1}\Post_{1j}}\\
+\set{\gamma''}=&\bigoplus_{i=1}^{n+1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{1} \Post_{1j} } }  \oplus  \vis{\set{\beta_2}\subst{\bigodot_{j=n+1}^{1}\Post_{1j}}} \oplus\\
+&\bigoplus_{i=1}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{1}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{1}\Post_{1j}} }
 \\
-\Pred=&\bigwedge_{i=0}^{n+1}\Pred_{1i}\subst{\bigodot_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j={n+1}}^{0}\Post_{1j}}\land\\ 
-&\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j={n+1}}^{0}\Post_{1j}}\Big)
+\Pred=&\bigwedge_{i=1}^{n+1}\Pred_{1i}\subst{\bigodot_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j={n+1}}^{1}\Post_{1j}}\land\\ 
+&\Big(\bigwedge_{i=1}^m\Pred_{3i}\subst{\bigodot_{j=i-1}^{1}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j={n+1}}^{1}\Post_{1j}}\Big)
 \\
-\Post=&\bigodot_{j=m}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j={n+1}}^{0}\Post_{1j}
+\Post=&\bigodot_{j=m}^{1}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j={n+1}}^{1}\Post_{1j}
 \end{align*}
@@
 
-These two cases above prove the implication with $n=-1$ and $m=-1$.
+These two cases above prove the implication with $n=0$ and $m=0$.
 
@@
 
-\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau open transitions such $n_1=n+m+3$, hence by simplification we have (strictly speaking, by induction we might also have the case $\alpha=\tau\land\set \gamma=\emptyset\land \ldots$ but in this case, rule \WTUn~ allows us to obtain a similar reduction with $n_1=1$):
+\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau open transitions such $n_1=n+m+1$, hence by simplification we have (strictly speaking, by induction we might also have the case $\alpha=\tau\land\set \gamma=\emptyset\land \ldots$ but in this case, rule \WTUn~ allows us to obtain a similar reduction with $n_1=1$):
 \begin{mathpar}
@@
 \Rightarrow \,
- \forall i \in [0..n_1].\openrule
+ \forall i \in [1..n_1].\openrule
     {
@@
 $ 
-s=s_{10} \wedge s_{1{(n_1+1)}}\!=s',\quad
-\displaystyle{\set{\gamma_1}= \bigoplus_{i=0}^{n_1} \vis{\set{\beta_{1 i}}\subst{\bigodot_{j=i-1}^{0} \Post_{1 j} } }} \\
-\Pred_1\!=\!\bigwedge_{i=0}^{n_1}(\Pred_{1i} \subst{\bigodot_{j=i-1}^{0}\Post_{i j}} ), \quad \Post_1= \bigodot_{i=n_1}^{0} \subst{\Post_{1i}} 
+s=s_{11} \wedge s_{1{(n_1+1)}}\!=s',\quad
+\displaystyle{\set{\gamma_1}= \bigoplus_{i=1}^{n_1} \vis{\set{\beta_{1 i}}\subst{\bigodot_{j=i-1}^{1} \Post_{1 j} } }} \\
+\Pred_1\!=\!\bigwedge_{i=1}^{n_1}(\Pred_{1i} \subst{\bigodot_{j=i-1}^{1}\Post_{i j}} ), \quad \Post_1= \bigodot_{i=n_1}^{1} \subst{\Post_{1i}} 
 $
 
-\item Similarly, a series of $m_1$ open transitions such that $m_1=n+m+3$   can be simplified as follows: 
+\item Similarly, a series of $m_1$ open transitions such that $m_1=n+m+1$   can be simplified as follows: 
 \begin{mathpar}
@@
 \Rightarrow\, 
-\forall i \in [0..m_1].\openrule
+\forall i \in [1..m_1].\openrule
     {
@@
 \begin{mathpar}
-s''=s_{30}
+s''=s_{31}
 
@@
 
-\displaystyle{\set{\gamma_3}= \bigoplus_{i=0}^{m_1} \vis{\set{\beta_{3 i}}\subst{\bigodot_{j=i-1}^{0} \Post_{3 j} } }}
+\displaystyle{\set{\gamma_3}= \bigoplus_{i=1}^{m_1} \vis{\set{\beta_{3 i}}\subst{\bigodot_{j=i-1}^{1} \Post_{3 j} } }}
 
@@
 
-\Pred_3\!=\!\bigwedge_{i=0}^{m_1}(\Pred_{3i} \subst{\bigodot_{j=i-1}^{0}\Post_{3 j}} )
+\Pred_3\!=\!\bigwedge_{i=1}^{m_1}(\Pred_{3i} \subst{\bigodot_{j=i-1}^{1}\Post_{3 j}} )
 
@@
 
- \Post_3= \bigodot_{i=m_1}^{0} \subst{\Post_{3i}} 
+ \Post_3= \bigodot_{i=m_1}^{1} \subst{\Post_{3i}} 
 \end{mathpar}
@@
 \Rightarrow 
-\bigg(\forall i \in [0..n_2].\openrule
+\bigg(\forall i \in [1..n_2].\openrule
     {
@@
  \wedge
-\forall i \in [0..m_2].\openrule
+\forall i \in [1..m_2].\openrule
          {
@@
 \begin{align*}
-s'=s_{20} &\wedge s_{2(n_2+1)}=s_2 \wedge  s_2' = s_{20}' \wedge s_{2(m_2+1)}'=s''\\
-\alpha''=&\alpha'\subst{\bigodot_{j=n_2}^{0}\Post_{2j}}\\
-\set{\gamma_2}=&\bigoplus_{i=0}^{n_2} \vis{\set{\beta_{2i}}\subst{\bigodot_{j=i-1}^{0} \Post_{2 j} } }  \oplus  \vis{\set{\beta'}\subst{\bigodot_{j=n_2}^{0}\Post_{2j}}} \oplus\\
+s'=s_{21} &\wedge s_{2(n_2+1)}=s_2 \wedge  s_2' = s_{21}' \wedge s_{2(m_2+1)}'=s''\\
+\alpha''=&\alpha'\subst{\bigodot_{j=n_2}^{1}\Post_{2j}}\\
+\set{\gamma_2}=&\bigoplus_{i=1}^{n_2} \vis{\set{\beta_{2i}}\subst{\bigodot_{j=i-1}^{1} \Post_{2 j} } }  \oplus  \vis{\set{\beta'}\subst{\bigodot_{j=n_2}^{1}\Post_{2j}}} \oplus\\
 &
- \bigoplus_{i=0}^{m_2} \vis{\set{\beta'_{2i}} \subst{\bigodot_{j=i-1}^{0}\Post\,'_{2j}\shortodot\Post\,'\shortodot\bigodot_{j=n_2}^{0}\Post_{2j}}}
+ \bigoplus_{i=1}^{m_2} \vis{\set{\beta'_{2i}} \subst{\bigodot_{j=i-1}^{1}\Post\,'_{2j}\shortodot\Post\,'\shortodot\bigodot_{j=n_2}^{1}\Post_{2j}}}
 \\
-\Pred_2=&\bigwedge_{i=0}^{n_2}\Pred_{2i}\subst{\bigodot_{j=i-1}^{0}\Post_{2j}}\land\Pred\,' \subst{\bigodot_{j={n_2}}^{0}\Post_{2j}}\land\\ 
-&\Big(\bigwedge_{i=0}^{m_2}\Pred\,'_{2i}\subst{\bigodot_{j=i-1}^{0}\Post\,'_{2j}\shortodot\Post\,'\shortodot\bigodot_{j={n_2}}^{0}\Post_{2j}}\Big)\\
-\Post_2=&\bigodot_{j=m_2}^{0}\Post\,'_{2j}\shortodot\Post\,'\shortodot\bigodot_{j={n_2}}^{0}\Post_{2j}
+\Pred_2=&\bigwedge_{i=1}^{n_2}\Pred_{2i}\subst{\bigodot_{j=i-1}^{1}\Post_{2j}}\land\Pred\,' \subst{\bigodot_{j={n_2}}^{1}\Post_{2j}}\land\\ 
+&\Big(\bigwedge_{i=1}^{m_2}\Pred\,'_{2i}\subst{\bigodot_{j=i-1}^{1}\Post\,'_{2j}\shortodot\Post\,'\shortodot\bigodot_{j={n_2}}^{1}\Post_{2j}}\Big)\\
+\Post_2=&\bigodot_{j=m_2}^{1}\Post\,'_{2j}\shortodot\Post\,'\shortodot\bigodot_{j={n_2}}^{1}\Post_{2j}
 \end{align*}
@@
  \Rightarrow
-\bigg(\forall i\in [0..(n_1\!+\!n_2)].\openrule
+\bigg(\forall i\in [1..(n_1\!+\!n_2)].\openrule
     {
@@
 \wedge\,
-\forall i \in [0..(m_1\!+\!m_2)].\openrule
+\forall i \in [1..(m_1\!+\!m_2)].\openrule
          {\set{\beta_{5i}},\Pred_{5 i},\Post_{5i}    }
@@
 s_{4i}=\begin{cases}
-			s_{1i} & \mbox{if }i<n_1\\
-			s_{2i-n_1} & \mbox{if }i\geq n_1
+			s_{1i} & \mbox{if }i\leq n_1\\
+			s_{2i-n_1} & \mbox{if }i> n_1
 	   \end{cases}
@@
 s_{5i}=\begin{cases}
-			s_{3i} & \mbox{if }i<m_1\\
-s_{2i-m_1}' & \mbox{if }i\geq m_1
+			s_{3i} & \mbox{if }i\leq m_1\\
+s_{2i-m_1}' & \mbox{if }i> m_1
 	\end{cases}\\
@@
 \begin{align*}
-s\!=\!s_{40}& ~\wedge~s_{4(n_1+n_2+1)}\!=s_2 ~\wedge~s_2' = s_{50} ~\wedge~ s_{5(m_1+m_2+1)}\!=\!s'\\
-\alpha''=&\alpha\subst{\!\!\bigodot_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}\\
-\set{\gamma}=&\bigoplus_{i=0}^{n_1+n_2} \vis{\set{\beta_{4i}}\subst{\bigodot_{j=i-1}^{0} \Post_{4 j} } }  \oplus  \vis{\set{\beta'}\subst{\!\!\bigodot_{j=n_1+n_2}^{0}\!\!\!\Post_{4j}}}\oplus \\
-&\bigoplus_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta_{5i}}\subst{\bigodot_{j=i-1}^{0}\Post\,'_{5i}\shortodot\Post\,'\shortodot\!\!\bigodot_{j=n_1+n_2}^{0}\!\!\!\Post_{4i}} }\\
+s\!=\!s_{41}& ~\wedge~s_{4(n_1+n_2+1)}\!=s_2 ~\wedge~s_2' = s_{51} ~\wedge~ s_{5(m_1+m_2+1)}\!=\!s'\\
+\alpha''=&\alpha\subst{\!\!\bigodot_{j=n_1+n_2}^{1}\!\!\!\Post_{4j}}\\
+\set{\gamma}=&\bigoplus_{i=1}^{n_1+n_2} \vis{\set{\beta_{4i}}\subst{\bigodot_{j=i-1}^{1} \Post_{4 j} } }  \oplus  \vis{\set{\beta'}\subst{\!\!\bigodot_{j=n_1+n_2}^{1}\!\!\!\Post_{4j}}}\oplus \\
+&\bigoplus_{i=1}^{m_1+m_2}\!\!\vis{\set{\beta_{5i}}\subst{\bigodot_{j=i-1}^{1}\Post\,'_{5i}\shortodot\Post\,'\shortodot\!\!\bigodot_{j=n_1+n_2}^{1}\!\!\!\Post_{4i}} }\\
 \Pred=&
-\bigwedge_{i=0}^{n_1+n_2}\!\!\Pred_{4i}\subst{\bigodot_{j=i-1}^{0}\Post_{4j}}\land\Pred\,' \subst{\!\!\bigodot_{j={n_1+n_2}}^{0}\!\!\!\Post_{4j}}\land\\ 
-&\quad\bigwedge_{i=0}^{m_1+m_2}\Pred_{5i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post_{5j}\shortodot\Post\,'\shortodot\!\!\!\bigodot_{j={n_1+n_2}}^{0}\!\!\!\Post_{4j}}\\
-\Post=&\bigodot_{j=m_1+m_2}^{0}\!\!\!\Post_{5j}\shortodot\Post\,'\shortodot\!\!\bigodot_{j={n_1+n_2}}^{0}\!\!\Post_{4j}
+\bigwedge_{i=1}^{n_1+n_2}\!\!\Pred_{4i}\subst{\bigodot_{j=i-1}^{1}\Post_{4j}}\land\Pred\,' \subst{\!\!\bigodot_{j={n_1+n_2}}^{1}\!\!\!\Post_{4j}}\land\\ 
+&\quad\bigwedge_{i=1}^{m_1+m_2}\Pred_{5i}\subst{\bigodot_{j=i-1}^{1}\!\!\Post_{5j}\shortodot\Post\,'\shortodot\!\!\!\bigodot_{j={n_1+n_2}}^{1}\!\!\!\Post_{4j}}\\
+\Post=&\bigodot_{j=m_1+m_2}^{1}\!\!\!\Post_{5j}\shortodot\Post\,'\shortodot\!\!\bigodot_{j={n_1+n_2}}^{1}\!\!\Post_{4j}
 \end{align*}
@@
          \Rightarrow
-\bigg(\forall i \in [0..n].\openrule
+\bigg(\forall i \in [1..n].\openrule
     {
@@
  \wedge\\
-\forall i \in [0..m].\openrule
+\forall i \in [1..m].\openrule
          {
@@
 \begin{align*}
-s=s_{10} &\wedge s_{1(n+1)}=s_{20} \wedge s_{21} = s_{30} \wedge s_{3(m+1)}=s'\\
-\alpha=&\alpha'\subst{\bigodot_{j=n}^{0}\Post_{1j}}\\
-\gamma_j^{j\in J'}=&\bigoplus_{i=0}^n \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{0} \Post_{1j} } }  \oplus  \vis{\set{\beta_2}\subst{\bigodot_{j=n}^{0}\Post_{1j}}} \oplus\\
-&\bigoplus_{i=0}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}} }
+s=s_{11} &\wedge s_{1(n+1)}=s_{20} \wedge s_{21} = s_{31} \wedge s_{3(m+1)}=s'\\
+\alpha=&\alpha'\subst{\bigodot_{j=n}^{1}\Post_{1j}}\\
+\gamma_j^{j\in J'}=&\bigoplus_{i=1}^n \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{1} \Post_{1j} } }  \oplus  \vis{\set{\beta_2}\subst{\bigodot_{j=n}^{1}\Post_{1j}}} \oplus\\
+&\bigoplus_{i=1}^m \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{1}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{1}\Post_{1j}} }
 \\
-\Pred_{OT}=&\bigwedge_{i=0}^n\Pred_{1i}\subst{\bigodot_{j=i-1}^{0}\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j=n}^{0}\Post_{1j}}\land\\ 
-&\qquad\Big(\bigwedge_{i=0}^m\Pred_{3i}\subst{\bigodot_{j=i-1}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}}\Big)\\
-\Post_{OT}=&\bigodot_{j=m}^{0}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{0}\Post_{1j}
+\Pred_{OT}=&\bigwedge_{i=1}^n\Pred_{1i}\subst{\bigodot_{j=i-1}^{1}\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j=n}^{1}\Post_{1j}}\land\\ 
+&\qquad\Big(\bigwedge_{i=1}^m\Pred_{3i}\subst{\bigodot_{j=i-1}^{1}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{1}\Post_{1j}}\Big)\\
+\Post_{OT}=&\bigodot_{j=m}^{1}\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=n}^{1}\Post_{1j}
 \end{align*}
 
-For the sake of simplicity, we prove the rule in the  restricted case where $n$ and $m$ are equal to $0$, hence a single tau open transition will be considered on each side of the potentially visible one.
+For the sake of simplicity, we prove the rule in the  restricted case where $n$ and $m$ are equal to $1$, hence a single tau open transition will be considered on each side of the potentially visible one.
 The proof may be easily generalized to the multiple tau open transitions by using the same reasoning and \WTTrois~ rule.
@@
        \beta_{1j}^{j\in J_1'},\Pred_1,\Post_1   }
-         {s_{10} \OTarrow {\tau} s_{11}}          
-\end{mathpar}
-by hypothesis we have $(s,t|\Pred_{s,t})\in\mathcal{R}$  and $s=s_{10}$.
+         {s_{11} \OTarrow {\tau} s_{12}}          
+\end{mathpar}
+by hypothesis we have $(s,t|\Pred_{s,t})\in\mathcal{R}$  and $s=s_{11}$.
 Thus, by  Definition \ref{def-Weak-bisim} we  can deduce there exists an indexed set of weak open transitions $\symb{WOT}_a^{a\in A} \subseteq \WT_2$:
@@
 \end{mathpar}
- such that  $\forall a, J_{a}=\{j\in J_1'|\beta_{1j}\neq\tau\},   (s_{11},u_a|\Pred_{s_{11},a})\in \mathcal{R}$ and \\
+ such that  $\forall a, J_{a}=\{j\in J_1'|\beta_{1j}\neq\tau\},   (s_{12},u_a|\Pred_{s_{11},a})\in \mathcal{R}$ and \\
  $\Pred_{s,t} \land \Pred_1\implies\\
@@
        \beta_{3j}^{j \in J_3'},\Pred_3,\Post_3   }
-         {s_{30} \OTarrow {\tau} s_{31}} \in \mathcal{T}          
-\end{mathpar}
-From previous case, we have $(s_{21},v_{b}|\Pred_{s_{21},b})\in \mathcal{R}$, and we have $s_{21}=s_{30}$. Then, by
+         {s_{31} \OTarrow {\tau} s_{32}} \in \mathcal{T}          
+\end{mathpar}
+From previous case, we have $(s_{21},v_{b}|\Pred_{s_{21},b})\in \mathcal{R}$, and we have $s_{21}=s_{31}$. Then, by
  Definition \ref{def-Weak-bisim} there exists an indexed set of weak open transitions $\symb{WOT}_{a}^{c\in C} \subseteq \WT_2$:
@@
 		 Then there exist $n$, $\Pred\,'$,  
-		$\Post\,'$,   and for all $p\in[0..n]$ there exist $\beta_p$, $\alpha_p$, $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
+		$\Post\,'$,   and for all $p\in[1..n]$ there exist $\beta_p$, $\alpha_p$, $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[1..n+1]$ $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
 		%\[
@@
 \text{\qquad and \qquad}\gamma_{j_0}=[\beta_0..\beta_n]
-	\vspace{-2.2ex}\\\text{and for all $p\in[0..n]$~~}
+	\vspace{-2.2ex}\\\text{and for all $p\in[1..n]$~~}
 		%\[
@@
 \\
-		\text{such that~\qquad}  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) 
+		\text{such that~\qquad}  \bigcup_{p=1}^nJ_{p} = J\cap\Holes(Q) 
 \text{, }
- \gamma_j^{j\in J\cap\Holes(Q)}= \bigoplus_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigodot_{i=p-1}^{0}\Post_i}, \\
+ \gamma_j^{j\in J\cap\Holes(Q)}= \bigoplus_{p=1}^n (\gamma_{p j}^{j\in J_p})\subst{\bigodot_{i=p-1}^{1}\Post_i}, \\
 {~}\Pred \iff \Pred\,'
-		\land \!\!\bigwedge_{p=0}^n(\alpha_p\subst{\bigodot_{i=p-1}^{0}\Post_i} = \beta_p\land \Pred_p\subst{\bigodot_{i=p-1}^{0}\Post_i} ),
+		\land \!\!\bigwedge_{p=1}^n(\alpha_p\subst{\bigodot_{i=p-1}^{1}\Post_i} = \beta_p\land \Pred_p\subst{\bigodot_{i=p-1}^{1}\Post_i} ),
 \\
-{~\hspace{2cm}}\Post=\Post\,' \uplus \bigodot_{p=n}^0
-		\Post_p,   \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\
+{~\hspace{2cm}}\Post=\Post\,' \uplus \bigodot_{p=n}^1
+		\Post_p,   \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{1 i} = s_i\\
 		\end{mathpar} 
@@
 By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
-$ \forall p\! \in [0..m_1]\,		
+$ \forall p\! \in [1..m_1]\,		
 	P[Q]_{j_0}\!\models		
@@
 and 
- $\forall p \in [0..m_2] \,\, P[Q]_{j_0}\!\models \openrule
+ $\forall p \in [1..m_2] \,\, P[Q]_{j_0}\!\models \openrule
          {
@@
 {\small \begin{align*}
-\forall l\in L.\,&s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l\\
-\alpha=&\alpha'{\subst{\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}}\\
-\gamma_j^{j\in J}=&\bigoplus_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{0}\!\! \Post_{1j}}}\oplus\\&  \vis{\set{\beta_2}\subst{\bigodot_{j=m_1}^{0}\Post_{1j}}} \oplus  
-{\bigoplus_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}} }}
+\forall l\in L.\,&s_l=s_{1 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{1 l} \wedge u_{(m_2+1) l}=s'_l\\
+\alpha=&\alpha'{\subst{\bigodot_{j=m_1}^{1}\!\!\Post_{1j}}}\\
+\gamma_j^{j\in J}=&\bigoplus_{i=1}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{1}\!\! \Post_{1j}}}\oplus\\&  \vis{\set{\beta_2}\subst{\bigodot_{j=m_1}^{1}\Post_{1j}}} \oplus  
+{\bigoplus_{i=1}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{1}\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{1}\!\!\Post_{1j}} }}
 \\
-\Pred=&\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}\land\\&
-\bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}\\
-\Post=&\bigodot_{j=m_2}^{0}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}
+\Pred=&\bigwedge_{i=1}^{m_1}\Pred_{1i}\subst{\bigodot_{j=i-1}^{1}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j=m_1}^{1}\!\!\Post_{1j}}\land\\&
+\bigwedge_{i=1}^{m_2}\Pred_{3i}\subst{\bigodot_{j=i-1}^{1}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{1}\!\!\Post_{1j}}\\
+\Post=&\bigodot_{j=m_2}^{1}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{1}\!\!\Post_{1j}
 \end{align*}}
@@
 				{\Post\,''_2}}
-			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_{20}}
+			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_{21}}
 				\ostate{t_l'^{\,l\in L_Q}}}
@@
 such that  $\Pred_2 \iff {\Pred\,'_2}
-		\land {\Pred\,''_2}\land \alpha_2=\beta_{2j_0}$, $\Post_2={\Post\,'_2}\uplus 
+		\land {\Pred\,''_2}\land \alpha_{2 0}=\beta_{2j_0}$, $\Post_2={\Post\,'_2}\uplus 
 		{\Post\,''_2}$ where ${\Post\,''_2}$ is the restriction of $\Post_2$ over variables  $\vars(Q)$.
@@
 \end{enumerate}
-By using  Lemma \ref{lem-rel-OT-WOT}, and denoting $\displaystyle{J=\bigcup_{i=0}^{m_1}J_{1i}\cup J_2\cup \bigcup_{i=0}^{m_2}J_{3i}}$, we can conclude from cases (1), (2) and (3) that we have:
+By using  Lemma \ref{lem-rel-OT-WOT}, and denoting $\displaystyle{J=\bigcup_{i=1}^{m_1}J_{1i}\cup J_2\cup \bigcup_{i=1}^{m_2}J_{3i}}$, we can conclude from cases (1), (2) and (3) that we have:
 \begin{mathpar}
@@
 where
-$\alpha''=\alpha'\displaystyle{\subst{\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}}}$\\
+$\alpha''=\alpha'\displaystyle{\subst{\bigodot_{j=m_1}^{1}\!\!\Post\,'_{1j}}}$\\
 On the other hand, we have:\\
-$\alpha=\alpha'\displaystyle{\subst{\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}}}\displaystyle{\subst{\bigodot_{j=m_1}^{0}\!\!\Post\,''_{1j}}}=\alpha''\displaystyle{\subst{\bigodot_{j=m_1}^{0}\!\!\Post\,''_{1j}}}$.\\
-As $\displaystyle{\subst{\bigodot_{j=m_1}^{0}\!\!\Post\,''_{1j}}}$ has no effect on variables of $P$ and thus on variables of $\alpha''$, so we have $\alpha=\alpha''$.
+$\alpha=\alpha'\displaystyle{\subst{\bigodot_{j=m_1}^{1}\!\!\Post\,'_{1j}}}\displaystyle{\subst{\bigodot_{j=m_1}^{1}\!\!\Post\,''_{1j}}}=\alpha''\displaystyle{\subst{\bigodot_{j=m_1}^{1}\!\!\Post\,''_{1j}}}$.\\
+As $\displaystyle{\subst{\bigodot_{j=m_1}^{1}\!\!\Post\,''_{1j}}}$ has no effect on variables of $P$ and thus on variables of $\alpha''$, so we have $\alpha=\alpha''$.
 
 {\small \begin{align*}
-\forall l\in L.\,&s_l=s_{0l} \wedge s_{(m_1+1)l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)l}=s'_l\\
-{(\gamma_j')}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}=&\displaystyle{\bigoplus_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{0}\!\!\Post\,'_{1j}}}\oplus  \vis{\set{\beta_{2}}\subst{\bigodot_{j=m_1}^{0}\Post\,'_{1j}}}} \oplus\\
-& \bigoplus_{i=0}^{m_2}
-\vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\!\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}} }
+\forall l\in L.\,&s_l=s_{1l} \wedge s_{(m_1+1)l}=t_l \wedge t'_l = u_{1l} \wedge u_{(m_2+1)l}=s'_l\\
+{(\gamma_j')}^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}=&\displaystyle{\bigoplus_{i=1}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{1}\!\!\Post\,'_{1j}}}\oplus  \vis{\set{\beta_{2}}\subst{\bigodot_{j=m_1}^{1}\Post\,'_{1j}}}} \oplus\\
+& \bigoplus_{i=1}^{m_2}
+\vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{1}\!\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{1}\!\!\Post\,'_{1j}} }
 \end{align*}}
 {\small \begin{align*}
-\Pred\,'=&\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}}\land\\ 
-&\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}}\\
-\Post'=&\bigodot_{j=m_2}^{0}\!\!\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}
+\Pred\,'=&\bigwedge_{i=1}^{m_1}\Pred\,'_{1i}\subst{\bigodot_{j=i-1}^{1}\!\!\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigodot_{j=m_1}^{1}\!\!\Post\,'_{1j}}\land\\ 
+&\bigwedge_{i=1}^{m_2}\Pred\,'_{3i}\subst{\bigodot_{j=i-1}^{1}\!\!\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{1}\!\!\Post\,'_{1j}}\\
+\Post'=&\bigodot_{j=m_2}^{1}\!\!\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{1}\!\!\Post\,'_{1j}
 \end{align*}}
@@
 $\begin{array}{l}\displaystyle{
-\Pred_\beta=\bigwedge_{p=0}^{m_1}(\beta_{1pj_0}=\alpha_{1p})\subst{\bigodot_{j=p-1}^{0}\!\!\Post_{1j}} \wedge (\beta_{2j_0}=\alpha_{20})\subst{\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}} \wedge \\\qquad\qquad
+\Pred_\beta=\bigwedge_{p=1}^{m_1}(\beta_{1pj_0}=\alpha_{1p})\subst{\bigodot_{j=p-1}^{1}\!\!\Post_{1j}} \wedge (\beta_{2j_0}=\alpha_{21})\subst{\bigodot_{j=m_1}^{1}\!\!\Post_{1j}}} \wedge \\\qquad\qquad
 \displaystyle{
-\bigwedge_{p=0}^{m_2}(\beta_{3pj_0}=\alpha_{3p})
-\subst{\bigodot_{j=p-1}^{0}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}}
+\bigwedge_{p=1}^{m_2}(\beta_{3pj_0}=\alpha_{3p})
+\subst{\bigodot_{j=p-1}^{1}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{1}\!\!\Post_{1j}}}
 \end{array}$
@@
 We proceed in the same way  for states named $u$.
-To simplify the proof, we suppose that in case 3, $Q$  moves, else transition 3 of $Q$ should be skipped and the last $s_{p l}$ are equal to the first $u_{0 l}$.
+To simplify the proof, we suppose that in case 3, $Q$  moves, else transition 3 of $Q$ should be skipped and the last $s_{p l}$ are equal to the first $u_{1 l}$.
 So we have: \\
 \begin{small}
-$\forall p\! \in\! [0..n_1]~ Q\models{\openrule
+$\forall p\! \in\! [1..n_1]~ Q\models{\openrule
 			{
@@
 and \\
-$\forall p \in [0..n_2]~ Q\models{\openrule
+$\forall p \in [1..n_2]~ Q\models{\openrule
 			{
@@
 
-$\forall p \in [0..(n_1\!+\!n_2\!+\!2)]\,\, Q\models{\openrule
+$\forall p \in [1..(n_1\!+\!n_2\!+\!1)]\,\, Q\models{\openrule
 			{
@@
 $\\ 
-In this equation, and using case 1 above for all $k\in [0\ldots n_1]$ there is a $p\in [0..m_1]$ such that $\alpha_{1p}=\alpha'_k$ (following the re-indexing done in the removal of steps where $Q$ does not move), we know that $\Pred_{1p}$ contains the predicate $( \alpha_{1p}=\beta_{1 p j_0})$.
+In this equation, and using case 1 above for all $k\in [1\ldots n_1]$ there is a $p\in [1..m_1]$ such that $\alpha_{1p}=\alpha'_k$ (following the re-indexing done in the removal of steps where $Q$ does not move), we know that $\Pred_{1p}$ contains the predicate $( \alpha_{1p}=\beta_{1 p j_0})$.
 Because $\beta_{1 p j_0}$ only contains variables of $P$ and $\alpha'_k$ only variables of $Q$, we have:
@@
 \begin{split}
-(\alpha_{1p}=\beta_{1pj_0})\subst{\bigodot_{j=p-1}^{0}\!\!\Post_{1j}}&\iff
-\alpha_{1p}\subst{\bigodot_{j=p-1}^{0}\!\!\Post\,''_{1j}}
-= \beta_{1 p j_0}\subst{\bigodot_{j=p-1}^{0}\!\!\Post\,'_{1j}} \\
-&\iff\alpha'_k\subst{\bigodot_{j=k-1}^{0}\!\!\Post\,''_{j}}= \beta_{1 p j_0}\subst{\bigodot_{j=p-1}^{0}\!\!\Post\,'_{1j}} 
+(\alpha_{1p}=\beta_{1pj_0})\subst{\bigodot_{j=p-1}^{1}\!\!\Post_{1j}}&\iff
+\alpha_{1p}\subst{\bigodot_{j=p-1}^{1}\!\!\Post\,''_{1j}}
+= \beta_{1 p j_0}\subst{\bigodot_{j=p-1}^{1}\!\!\Post\,'_{1j}} \\
+&\iff\alpha'_k\subst{\bigodot_{j=k-1}^{1}\!\!\Post\,''_{j}}= \beta_{1 p j_0}\subst{\bigodot_{j=p-1}^{1}\!\!\Post\,'_{1j}} 
 \end{split}
@@
 \Pred_\beta \iff \gamma_{j_0}=
-\vis{[\alpha'_{p}\subst{\bigodot_{j=p-1}^{0}\!\!\Post\,''_{j}}|p\in[0..n_1+n_2+2]]}
+\vis{[\alpha'_{p}\subst{\bigodot_{j=p-1}^{1}\!\!\Post\,''_{j}}|p\in[1..n_1+n_2+1]]}
 \end{equation}
@@
 
-Let us consider the sequence of $(n_1+n_2+3)$  actions $\alpha'_p$ some of them may be non-observable (they are $\tau$ transitions).
+Let us consider the sequence of $(n_1+n_2+1)$  actions $\alpha'_p$ some of them may be non-observable (they are $\tau$ transitions).
 By considering the sequence of $\tau$ and non-$\tau$ actions we split the sequence of actions into $n+1$ sub-sequences, such that each sub-sequence is a sequence of actions containing  only one observable action that will be named $\alpha_p$, and possibly many non-observable ($\tau$) ones.
@@
 For $k\in [0..n]$ the position of the $k^{\text{th}}$ visible action is  $n_k$.
-For $l\in [1..n]$,  $n'_l$ is any index between $n_{l-1}$ and $n_l$, additionally $n'_0=0$ and $n'_{n+1}=n_1+n_2+3$.
-We obtain $n+1$ sub-sequences  made of the following OTs, for all $k\in [0..n]$ :\\
+For $l\in [1..n]$,  $n'_l$ is any index between $n_{l-1}$ and $n_l$, additionally $n'_1=1$ and $n'_{n+1}=n_1+n_2+1$.
+We obtain $n$ sub-sequences  made of the following OTs, for all $k\in [1..n]$ :\\
 \begin{small}
@@
 
-\noindent Note that for all $k\in[0..n-1]$, $v_{kl}'=v_{(k+1)l}$,  $v_{0l}=s_{0l}=s_l$, and $v'_{nl}=v_{(n_1+n_2+3) l}=u_{(n_2+1) l} = s'_l$.
-
-\noindent By definition of $\Post_k$, we have $\displaystyle{\bigodot_{j=n'_{k}-1}^{0}\!\!\Post\,''_{j} = \bigodot_{j=k-1}^{0}\!\!\Post_{j}}$.
+\noindent Note that for all $k\in[1..n-1]$, $v_{kl}'=v_{(k+1)l}$,  $v_{1l}=s_{1l}=s_l$, and $v'_{nl}=v_{(n_1+n_2+3) l}=u_{(n_2+1) l} = s'_l$.
+
+\noindent By definition of $\Post_k$, we have $\displaystyle{\bigodot_{j=n'_{k}-1}^{1}\!\!\Post\,''_{j} = \bigodot_{j=k-1}^{1}\!\!\Post_{j}}$.
 %In this case, the number of weak open transitions
@@
 Consequently,  we have:
-\[\alpha'_{n_k}{\subst{\!\bigodot_{j=n_k-1}^{0}\!\!\!\!\Post\,''_{j}}} \!=\!
-\alpha'_{n_k}\displaystyle{\subst{\!\!\bigodot_{j=n_k-1}^{n'_{k}}\!\!\!\!\Post''_{j}\odot\!\!\!\!\bigodot_{j=n'_{k}-1}^{0}\!\!\!\!\Post\,''_{j}}} \!=\!
-\alpha_k\displaystyle{\subst{\!\!\bigodot_{j=n'_{k}-1}^{0}\!\!\!\Post\,''_{j}}} \!=\!
-\alpha_k\displaystyle{\subst{\!\bigodot_{j=k-1}^{0}\!\!\Post_{j}}}\]
+\[\alpha'_{n_k}{\subst{\!\bigodot_{j=n_k-1}^{1}\!\!\!\!\Post\,''_{j}}} \!=\!
+\alpha'_{n_k}\displaystyle{\subst{\!\!\bigodot_{j=n_k-1}^{n'_{k}}\!\!\!\!\Post''_{j}\odot\!\!\!\!\bigodot_{j=n'_{k}-1}^{1}\!\!\!\!\Post\,''_{j}}} \!=\!
+\alpha_k\displaystyle{\subst{\!\!\bigodot_{j=n'_{k}-1}^{1}\!\!\!\Post\,''_{j}}} \!=\!
+\alpha_k\displaystyle{\subst{\!\bigodot_{j=k-1}^{1}\!\!\Post_{j}}}\]
 From equation~\ref{eqproofbeta}, we obtain the following equation (we recall that the actions $\alpha_k$ are the actions $\alpha'_{p}$ that are observable): 
@@
 \Pred_\beta &\iff& \gamma_{j_0}\!=\!
-\bigoplus_{p=0}^{p=n_1+n_2+2}
-\vis{\alpha'_{p}\subst{\bigodot_{j=p-1}^{0}\!\!\Post_{j}}}\\
+\bigoplus_{p=1}^{p=n_1+n_2+2}
+\vis{\alpha'_{p}\subst{\bigodot_{j=p-1}^{1}\!\!\Post_{j}}}\\
 %&\iff&\gamma_{j_0}=
@@
 &\iff& \gamma_{j_0}=
-[\alpha_{p}\subst{\bigodot_{j=p-1}^{0}\!\!\Post_{j}}|p\in[0..n]]
+[\alpha_{p}\subst{\bigodot_{j=p-1}^{1}\!\!\Post_{j}}|p\in[1..n]]
 \end{eqnarray*}
@@
 with
-\[  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) \qquad\text{trivial}\]
-\[ \gamma_j^{j\in J\cap\Holes(Q)}= \bigoplus_{p=0}^n (\gamma_{p j}^{j\in J_p})\subst{\bigodot_{i=p-1}^{0}\Post_i)}\]
+\[  \bigcup_{p=1}^nJ_{p} = J\cap\Holes(Q) \qquad\text{trivial}\]
+\[ \gamma_j^{j\in J\cap\Holes(Q)}= \bigoplus_{p=1}^n (\gamma_{p j}^{j\in J_p})\subst{\bigodot_{i=p-1}^{1}\Post_i)}\]
 Indeed we have:
@@
 \begin{split}
-\gamma_j^{j\in J}=&\bigoplus_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{0}\!\!
-\Post_{1j}}}\oplus  \vis{\set{\beta_2}\subst{\bigodot_{j=m_1}^{0}\Post_{1j}}} \oplus\\& \bigoplus_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{0}\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}} }\\
+\gamma_j^{j\in J}=&\bigoplus_{i=1}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigodot_{j=i-1}^{1}\!\!
+\Post_{1j}}}\oplus  \vis{\set{\beta_2}\subst{\bigodot_{j=m_1}^{1}\Post_{1j}}} \oplus\\& \bigoplus_{i=1}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigodot_{j=i-1}^{1}\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{1}\!\!\Post_{1j}} }\\
 \end{split}\end{equation*}
@@
 \begin{split}
-\gamma_j^{j\in J\cap \Holes(Q)}&=\bigoplus_{i=0}^{m_1} \vis{\set{(\beta_{1i}')}\subst{\bigodot_{j=i-1}^{0}\!\!
-\Post''_{1j}}}\oplus  \vis{\set{\beta'_2}\subst{\bigodot_{j=m_1}^{0}\Post''_{1j}}} \oplus\\&\qquad\qquad \bigoplus_{i=0}^{m_2} \vis{\set{\beta'_{3i}} \subst{\bigodot_{j=i-1}^{0}\!\Post''_{3j}\shortodot\Post''_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post''_{1j}} }\\
-&=\bigoplus_{k=0}^n \left( \bigoplus_{i=n'_k}^{n'_{k+1}-1}\vis{\beta_{ij}^{j\in J\cap \Holes(Q)}\subst{\bigodot_{j=i-1}^{n'_k}\!\!\Post''_{j}\bigodot_{j=n'_k-1}^{0}\!\!\Post''_{j}}}\right)\\
-&=\bigoplus_{k=0}^n \left( \gamma_{kj}^{j\in J\cap \Holes(Q)}\subst{\bigodot_{j=k-1}^{0}\!\!\Post_{k}}\right)
+\gamma_j^{j\in J\cap \Holes(Q)}&=\bigoplus_{i=1}^{m_1} \vis{\set{(\beta_{1i}')}\subst{\bigodot_{j=i-1}^{1}\!\!
+\Post''_{1j}}}\oplus  \vis{\set{\beta'_2}\subst{\bigodot_{j=m_1}^{1}\Post''_{1j}}} \oplus\\&\qquad\qquad \bigoplus_{i=1}^{m_2} \vis{\set{\beta'_{3i}} \subst{\bigodot_{j=i-1}^{1}\!\Post''_{3j}\shortodot\Post''_2\shortodot\bigodot_{j=m_1}^{1}\!\!\Post''_{1j}} }\\
+&=\bigoplus_{k=1}^n \left( \bigoplus_{i=n'_k}^{n'_{k+1}-1}\vis{\beta_{ij}^{j\in J\cap \Holes(Q)}\subst{\bigodot_{j=i-1}^{n'_k}\!\!\Post''_{j}\bigodot_{j=n'_k-1}^{1}\!\!\Post''_{j}}}\right)\\
+&=\bigoplus_{k=1}^n \left( \gamma_{kj}^{j\in J\cap \Holes(Q)}\subst{\bigodot_{j=k-1}^{1}\!\!\Post_{k}}\right)
 \end{split}\end{equation*}
@@
 \[\Pred = \displaystyle{\Pred\,'
-		\land \!\!\bigwedge_{p=0}^n\Big((\alpha_p\subst{\bigodot_{i=p-1}^{0}\Post_i}) = \beta_p\land (\Pred_p\subst{\bigodot_{i=p-1}^{0}\Post_i}) \Big)}\]
+		\land \!\!\bigwedge_{p=1}^n\Big((\alpha_p\subst{\bigodot_{i=p-1}^{1}\Post_i}) = \beta_p\land (\Pred_p\subst{\bigodot_{i=p-1}^{1}\Post_i}) \Big)}\]
 Indeed we have:
@@
 \begin{align*}
-\Pred&\iff\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}\land
-\bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}\\
-&\iff\bigwedge_{i=0}^{m_1}\left(\Pred\,'_{1i}
-		\land {\Pred\,''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}\right)\subst{\bigodot_{j=i-1}^{0}\!\!\Post_{1j}} \\
+\Pred&\iff\bigwedge_{i=1}^{m_1}\Pred_{1i}\subst{\bigodot_{j=i-1}^{1}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigodot_{j=m_1}^{1}\!\!\Post_{1j}}\land
+\bigwedge_{i=1}^{m_2}\Pred_{3i}\subst{\bigodot_{j=i-1}^{1}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{1}\!\!\Post_{1j}}\\
+&\iff\bigwedge_{i=1}^{m_1}\left(\Pred\,'_{1i}
+		\land {\Pred\,''_{1i}}\land \alpha_{1i}=\beta_{1ij_0}\right)\subst{\bigodot_{j=i-1}^{1}\!\!\Post_{1j}} \\
 &\qquad\land\left(\Pred\,'_{2}
-		\land {\Pred\,''_{2}}\land \alpha_{20}=\beta_{2j_0}\right)\subst{\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}\\
-&\qquad\land\bigwedge_{i=0}^{m_2} \left(\Pred\,'_{3i}
-		\land {\Pred\,''_{3i}}\land \alpha_{3i}=\beta_{3ij_0}\right) \subst{\bigodot_{j=i-1}^{0}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}\displaybreak[0]\\
-&\iff\bigwedge_{i=0}^{m_1}\left((\Pred\,'_{1i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post\,'_{1j}})
-		\land ({\Pred\,''_{1i}}\subst{\bigodot_{j=i-1}^{0}\!\!\Post\,''_{1j}})\land (\alpha_{1i}=\beta_{1ij_0})\subst{\bigodot_{j=i-1}^{0}\!\!\Post_{1j}}\right) \\
-&\qquad\land \left(\Pred\,'_{2}\subst{\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}
-		\land {\Pred\,''_{2}} \subst{\bigodot_{j=m_1}^{0}\!\!\Post_{1j}} \land (\alpha_{20}=\beta_{2j_0})\subst{\bigodot_{j=m_1}^{0}\!\!\Post_{1j}} \right) \\
-&\qquad\land\bigwedge_{i=0}^{m_2} \Bigg(\Pred\,'_{3i} \subst{\bigodot_{j=i-1}^{0}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}} 
-		\land {\Pred\,''_{3i}} \subst{\bigodot_{j=i-1}^{0}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}  \\
-		 & \qquad \land (\alpha_{3i}=\beta_{3ij_0}) \subst{\bigodot_{j=i-1}^{0}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}}\Bigg)  \\
-&\iff \Pred\,'\land\bigwedge_{k=0}^n\Pred_k\subst{\bigodot_{j=k-1}^{0}\!\!\Post_{j}}\land\Pred_\beta
-\\&\iff \Pred\,'\land\bigwedge_{k=0}^n\Pred_k\subst{\bigodot_{j=k-1}^{0}\!\!\Post_{j}}\land
-(\gamma_{j_0}=[\alpha_{i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post_{j}}|i\in[0..n]])
+		\land {\Pred\,''_{2}}\land \alpha_{21}=\beta_{2j_0}\right)\subst{\bigodot_{j=m_1}^{1}\!\!\Post_{1j}}\\
+&\qquad\land\bigwedge_{i=1}^{m_2} \left(\Pred\,'_{3i}
+		\land {\Pred\,''_{3i}}\land \alpha_{3i}=\beta_{3ij_0}\right) \subst{\bigodot_{j=i-1}^{0}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{1}\!\!\Post_{1j}}\displaybreak[0]\\
+&\iff\bigwedge_{i=1}^{m_1}\left((\Pred\,'_{1i}\subst{\bigodot_{j=i-1}^{1}\!\!\Post\,'_{1j}})
+		\land ({\Pred\,''_{1i}}\subst{\bigodot_{j=i-1}^{1}\!\!\Post\,''_{1j}})\land (\alpha_{1i}=\beta_{1ij_0})\subst{\bigodot_{j=i-1}^{1}\!\!\Post_{1j}}\right) \\
+&\qquad\land \left(\Pred\,'_{2}\subst{\bigodot_{j=m_1}^{1}\!\!\Post_{1j}}
+		\land {\Pred\,''_{2}} \subst{\bigodot_{j=m_1}^{1}\!\!\Post_{1j}} \land (\alpha_{21}=\beta_{2j_0})\subst{\bigodot_{j=m_1}^{1}\!\!\Post_{1j}} \right) \\
+&\qquad\land\bigwedge_{i=1}^{m_2} \Bigg(\Pred\,'_{3i} \subst{\bigodot_{j=i-1}^{1}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{1}\!\!\Post_{1j}} 
+		\land {\Pred\,''_{3i}} \subst{\bigodot_{j=i-1}^{1}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{1}\!\!\Post_{1j}}  \\
+		 & \qquad \land (\alpha_{3i}=\beta_{3ij_0}) \subst{\bigodot_{j=i-1}^{1}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{1}\!\!\Post_{1j}}\Bigg)  \\
+&\iff \Pred\,'\land\bigwedge_{k=1}^n\Pred_k\subst{\bigodot_{j=k-1}^{1}\!\!\Post_{j}}\land\Pred_\beta
+\\&\iff \Pred\,'\land\bigwedge_{k=1}^n\Pred_k\subst{\bigodot_{j=k-1}^{1}\!\!\Post_{j}}\land
+(\gamma_{j_0}=[\alpha_{i}\subst{\bigodot_{j=i-1}^{1}\!\!\Post_{j}}|i\in[1..n]])
 \end{align*}
@@
 Finally we have~~
-$\Post=\displaystyle{\Post\,' \uplus \bigodot_{p=n}^0
+$\Post=\displaystyle{\Post\,' \uplus \bigodot_{p=n}^1
 		\Post_p}$\quad
@@
 {\small \begin{align*}
-\Post&=\bigodot_{j=m_2}^{0}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post_{1j}\\
-&=\bigodot_{j=m_2}^{0}\!\!\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j} \uplus \bigodot_{j=m_2}^{0}\!\!\Post\,''_{3j}\shortodot\Post\,''_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post\,''_{1j}\\
-&=\Post\,' \uplus \bigodot_{j=n'_{n+1}-1}^{0}\!\!\Post\,''_{j}
+\Post&=\bigodot_{j=m_2}^{1}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=m_1}^{1}\!\!\Post_{1j}\\
+&=\bigodot_{j=m_2}^{1}\!\!\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{1}\!\!\Post\,'_{1j} \uplus \bigodot_{j=m_2}^{1}\!\!\Post\,''_{3j}\shortodot\Post\,''_2\shortodot\bigodot_{j=m_1}^{1}\!\!\Post\,''_{1j}\\
+&=\Post\,' \uplus \bigodot_{j=n'_{n+1}-1}^{1}\!\!\Post\,''_{j}
 \end{align*}}
-Which concludes because  we have $\displaystyle{\bigodot_{j=n'_{k}-1}^{0}\!\!\Post\,''_{j} = \bigodot_{j=k-1}^{0}\!\!\Post_{j}}$.
+Which concludes because  we have $\displaystyle{\bigodot_{j=n'_{k}-1}^{1}\!\!\Post\,''_{j} = \bigodot_{j=k-1}^{1}\!\!\Post_{j}}$.
 %
@@
 \begin{mathpar}
-\forall h\!\in\![0..k].Q\models\openrule
+\forall h\!\in\![1..k].Q\models\openrule
     {\set{\beta_{1h}},\Pred_{1h},\Post_{1h}   }
@@
 		\Post_2}
-	{\ostate{s_{20}}\OTarrow {\alpha'_Q}
-		\ostate{s_{21}}}
+	{\ostate{s_{21}}\OTarrow {\alpha'_Q}
+		\ostate{s_{22}}}
 }, \\ \quad\text{~~and~~}\quad 
-\forall h \in [0..k'].Q\models\openrule
+\forall h \in [1..k'].Q\models\openrule
          {
@@
 \begin{small}
-$s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$
+$s_i^{i\in L_Q}=s_{11} \wedge s_{1(k+1) i}=s_{21} \wedge  s_{22}= s_{31} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$
 \begin{align*}
-\alpha_Q=&\alpha'_Q\displaystyle{\subst{\bigodot_{j=k}^{0}\Post_{1j}}}
+\alpha_Q=&\alpha'_Q\displaystyle{\subst{\bigodot_{j=k}^{1}\Post_{1j}}}
 \end{align*}
 \begin{align*}
-\set{\gamma}=&\bigoplus_{h=0}^k \vis{\set{\beta_{1h}}\subst{\!\!\bigodot_{j=h-1}^{0}\!\! \Post_{1j} } }  \oplus  \vis{\set{\beta_2}\subst{\bigodot_{j=k}^{0}\!\!\Post_{1j}}} \oplus\\&
+\set{\gamma}=&\bigoplus_{h=1}^k \vis{\set{\beta_{1h}}\subst{\!\!\bigodot_{j=h-1}^{1}\!\! \Post_{1j} } }  \oplus  \vis{\set{\beta_2}\subst{\bigodot_{j=k}^{1}\!\!\Post_{1j}}} \oplus\\&
 		%&
- \bigoplus_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\!\!\bigodot_{j=h-1}^{0}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=k}^{0}\Post_{1j}} }\\
-\Pred_Q=&\bigwedge_{h=0}^{k}\!\Pred_{1h}\subst{\!\!\bigodot_{j=h-1}^{0}\!\!\!\!\Post_{1 j}}\land \Pred_2\subst{\bigodot_{h=k}^{0}\Post_{1h}}\land\\
+ \bigoplus_{h=1}^{k'} \vis{\set{\beta_{3h}} \subst{\!\!\bigodot_{j=h-1}^{1}\!\!\Post_{3j}\shortodot\Post_2\shortodot\bigodot_{j=k}^{1}\Post_{1j}} }\\
+\Pred_Q=&\bigwedge_{h=01}^{k}\!\Pred_{1h}\subst{\!\!\bigodot_{j=h-1}^{1}\!\!\!\!\Post_{1 j}}\land \Pred_2\subst{\bigodot_{h=k}^{1}\Post_{1h}}\land\\
 &
-	\!\bigwedge_{h=0}^{k'}\!\Pred_{3h}\subst{\!\! 	\bigodot_{j=h-1}^{0}\!\!\!{\Post_{3j}}\odot{\Post_2}  \odot\bigodot_{h=k}^{0}\!\!\Post_{1h}}\\
-\Post_Q=&\bigodot_{h=k'}^{0}\!\!\Post_{3h}\odot\Post_2\odot\bigodot_{j=k}^{0}\!\!\Post_{1j}
+	\!\bigwedge_{h=1}^{k'}\!\Pred_{3h}\subst{\!\! 	\bigodot_{j=h-1}^{1}\!\!\!{\Post_{3j}}\odot{\Post_2}  \odot\bigodot_{h=k}^{1}\!\!\Post_{1h}}\\
+\Post_Q=&\bigodot_{h=k'}^{1}\!\!\Post_{3h}\odot\Post_2\odot\bigodot_{j=k}^{1}\!\!\Post_{1j}
 \end{align*}
@@
 			\Post\uplus \Post_2}
-{\ostate{s^{i\in L}_{i}\uplus s_{20}} \OTarrow {\alpha} \ostate{{s'}^{i\in L}_{i}\uplus s_{21}}}
+{\ostate{s^{i\in L}_{i}\uplus s_{21}} \OTarrow {\alpha} \ostate{{s'}^{i\in L}_{i}\uplus s_{22}}}
 	}
@@
 \Post_c}
-         {\ostate{s_{10}\uplus s^{i\in L}_{i}} \OTWeakarrow {\alpha'} 
+         {\ostate{s_{11}\uplus s^{i\in L}_{i}} \OTWeakarrow {\alpha'} 
 	\ostate{{{s'}^{i\in L}_{i}\uplus s_{3(k'+1)}}}}\] 
 where ~~
-$\alpha'=\alpha\displaystyle{\subst{\bigodot_{j=k}^{0}\Post_{1j}}}$
+$\alpha'=\alpha\displaystyle{\subst{\bigodot_{j=k}^{1}\Post_{1j}}}$
 and $\alpha=\alpha'$  because $\Post_{1j}$ acts on variables of $Q$ and $\alpha$ contains only variables of $P$.
@@
 \begin{align*}
-\set{\gamma_c}=&\bigoplus_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigodot_{i=h-1}^{0}\!\!
-\Post_{1i} } }  \oplus  \vis{({\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2})\subst{\bigodot_{i=k}^{0}\Post_{1i}}} \oplus\\
-&\bigoplus_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigodot_{i=h-1}^{0}\!\!\Post_{3i}\shortodot\Post_2\shortodot\bigodot_{i=k}^{0}\Post_{1i}} }\\
+\set{\gamma_c}=&\bigoplus_{h=1}^k \vis{\set{\beta_{1h}}\subst{\bigodot_{i=h-1}^{1}\!\!
+\Post_{1i} } }  \oplus  \vis{({\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2})\subst{\bigodot_{i=k}^{1}\Post_{1i}}} \oplus\\
+&\bigoplus_{h=1}^{k'} \vis{\set{\beta_{3h}} \subst{\bigodot_{i=h-1}^{1}\!\!\Post_{3i}\shortodot\Post_2\shortodot\bigodot_{i=k}^{1}\Post_{1i}} }\\
 =&\set{\gamma}\uplus\vis{\beta_j^{\in J\setminus \{j_0\}}} \quad  \text{ because $\Post_{1j}$  does not act on variables of $\beta_j$.}  
@@
 \Pred_c=&
-\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigodot_{i=h-1}^{0}\Post_{1i}}\land
-\left(Pred\land\Pred_2\land \alpha'_Q=\beta_{j_0}\right) \subst{\bigodot_{i=k}^{0}{\Post_{1i}}}\land\\
-&\bigwedge_{h=0}^{k'}{\Pred_{3h}}\subst{\bigodot_{i=h-1}^{0}{\Post_{3i}}\shortodot({\Post\uplus \Post_2})\shortodot\bigodot_{i=k}^{0}{\Post_{1i}}}
+\bigwedge_{h=1}^k{\Pred_{1h}}\subst{\bigodot_{i=h-1}^{1}\Post_{1i}}\land
+\left(Pred\land\Pred_2\land \alpha'_Q=\beta_{j_0}\right) \subst{\bigodot_{i=k}^{1}{\Post_{1i}}}\land\\
+&\bigwedge_{h=1}^{k'}{\Pred_{3h}}\subst{\bigodot_{i=h-1}^{1}{\Post_{3i}}\shortodot({\Post\uplus \Post_2})\shortodot\bigodot_{i=k}^{1}{\Post_{1i}}}
 \\
-\Post_c=&(\bigodot_{i=k'}^{0}{\Post_{3i}})\shortodot({\Post\uplus \Post_2})\shortodot\bigodot_{i=k}^{0}{\Post_{1i}}
+\Post_c=&(\bigodot_{i=k'}^{1}{\Post_{3i}})\shortodot({\Post\uplus \Post_2})\shortodot\bigodot_{i=k}^{1}{\Post_{1i}}
 \end{align*}
 \end{small}
-\noindent Note that we have $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$.
+\noindent Note that we have $s_i^{i\in L_Q}=s_{11} \wedge s_{1(k+1) i}=s_{21} \wedge  s_{22}= s_{31} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$.
 
@@
 \begin{split}
-\Pred_c&=\Pred_Q\land\Pred\subst{\bigodot_{i=k}^{0}{\Post_{1i}}}\land
-(\alpha'_Q=\beta_{j_0})\subst{\bigodot_{i=k}^{0}{\Post_{1i}}}\\
+\Pred_c&=\Pred_Q\land\Pred\subst{\bigodot_{i=k}^{1}{\Post_{1i}}}\land
+(\alpha'_Q=\beta_{j_0})\subst{\bigodot_{i=k}^{1}{\Post_{1i}}}\\
 &=\Pred_Q\land\Pred\land \alpha_Q=\beta_{j_0}\\[.3ex]
@@
 }
-\qquad\text{~~and for all $p\in[0..n]$~~}\quad
+\quad\text{~~and $\forall p\in[1..n]$~~}
 Q\models{\openrule
@@
 \begin{mathpar}
-J_Q=\displaystyle{\bigcup_{p=0}^nJ_{p}}
+J_Q=\displaystyle{\bigcup_{p=1}^nJ_{p}}
 
@@
 
-\forall j\in J_p,\,\gamma_j= \displaystyle{\bigoplus_{p=0}^n \gamma_{p j}\subst{\bigodot_{k=p}^{0}{\Post_k}}}
-
-\Pred\,'=\Pred\land \bigwedge_{p=0}^{n}(\alpha_p=\beta_p\land \Pred_p)\subst{\bigodot_{i=p-1}^{0}\Post_i}
-
-\Post\,'=\Post\uplus\bigodot_{p=n}^{0}
+\forall j\in J_p,\,\gamma_j= \displaystyle{\bigoplus_{p=1}^n \gamma_{p j}\subst{\bigodot_{k=p}^{1}{\Post_k}}}
+
+\Pred\,'=\Pred\land \bigwedge_{p=1}^{n}(\alpha_p=\beta_p\land \Pred_p)\subst{\bigodot_{i=p-1}^{1}\Post_i}
+
+\Post\,'=\Post\uplus\bigodot_{p=n}^{1}
 		\Post_p
@@
 \begin{small}
-$\forall p\!\in\![0\,..\,m_1].P\models\openrule
+$\forall p\!\in\![1\,..\,m_1].P\models\openrule
     {{\beta_{1pj}^{j\in J_{1p}}},\Pred_{1p},\Post_{1p}   }
@@
          {\beta_{2j}^{j\in J_2},\Pred_2,\Post_2 }
-         {\ostate{({s_{20i}})^{i\in L}} \OTarrow {\alpha'} \ostate{({s_{21i}})^{i\in L}}} $ 
+         {\ostate{({s_{21i}})^{i\in L}} \OTarrow {\alpha'} \ostate{({s_{22i}})^{i\in L}}} $ 
 \\
-and  $\forall p \in [0\,..\,m_2].P\models\openrule
+and  $\forall p \in [1\,..\,m_2].P\models\openrule
          {
@@
 \begin{align*}
-\forall i\in L.&~~s_i=s_{10 i} \wedge s_{1(m_1+1) i}=s_{20i} \wedge  s_{21i}= s_{30 i} \wedge s_{3(m_2+1) i}=s'_i\\
-\alpha=&\alpha'{\subst{\bigodot_{j=m_1}^{0}\Post_{1j}}} \\
-\gamma_j^{j\in J}=&{\bigoplus_{i=0}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigodot_{k=i-1}^{0}\!\!
-\Post_{1k} } }  \oplus \, \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigodot_{k=m_1}^{0}\Post_{1k}}}}\, \oplus\\
-&\bigoplus_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{3p}} \subst{\bigodot_{k=i-1}^{0}\Post_{3k}\shortodot\Post_2\shortodot\bigodot_{k=m_1}^{0}\Post_{1k}}}\\
-\Pred=&{\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\subst{\!\bigodot_{j=p-1}^{0}\!\!\Post_{1j}}\big)\land\Pred_2\subst{\!\bigodot_{p=m_1}^{0}\!\!\Post_{1p}}\land}\\ 
+\forall i\in L.&~~s_i=s_{11 i} \wedge s_{1(m_1+1) i}=s_{21i} \wedge  s_{22i}= s_{31 i} \wedge s_{3(m_2+1) i}=s'_i\\
+\alpha=&\alpha'{\subst{\bigodot_{j=m_1}^{1}\Post_{1j}}} \\
+\gamma_j^{j\in J}=&{\bigoplus_{i=1}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigodot_{k=i-1}^{1}\!\!
+\Post_{1k} } }  \oplus \, \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigodot_{k=m_1}^{10}\Post_{1k}}}}\, \oplus\\
+&\bigoplus_{i=1}^{m_2} \vis{\beta_{3ij}^{j\in J_{3p}} \subst{\bigodot_{k=i-1}^{1}\Post_{3k}\shortodot\Post_2\shortodot\bigodot_{k=m_1}^{1}\Post_{1k}}}\\
+\Pred=&{\bigwedge_{p=1}^{m_1}\!\big(\Pred_{1p}\subst{\!\bigodot_{j=p-1}^{1}\!\!\Post_{1j}}\big)\land\Pred_2\subst{\!\bigodot_{p=m_1}^{1}\!\!\Post_{1p}}\land}\\ 
 &
-{\bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\bigodot_{j=p-1}^{0}\!\!\Post_{3j}\odot\Post_2 \odot\!\bigodot_{p=m_1}^{0}\!\!\Post_{1p}}}\\
-\Post=&{\bigodot_{p=m_2}^{0}\Post_{3p}\odot\Post_2\odot\bigodot_{j=m_1}^{0}\Post_{1j}}
+{\bigwedge_{p=1}^{m_2}\!\Pred_{3p}\subst{\!\bigodot_{j=p-1}^{1}\!\!\Post_{3j}\odot\Post_2 \odot\!\bigodot_{p=m_1}^{1}\!\!\Post_{1p}}}\\
+\Post=&{\bigodot_{p=m_2}^{1}\Post_{3p}\odot\Post_2\odot\bigodot_{j=m_1}^{1}\Post_{1j}}
 \end{align*}
@@
 
-We introduce $n_i^{i\in[0..m-1]}$, and $(n'_i)^{i\in[m+1..n]}$ the indices of the steps in 
+We introduce $n_i^{i\in[1..m-1]}$, and $(n'_i)^{i\in[m+1..n]}$ the indices of the steps in 
 which the hole $j_0$ moves in the 3 sets of OTs above ($\beta_m$ is the action that matches the hole $j_0$ in the OT $\alpha'$), in other words, we have for all $i$, $\beta_{1 n_i j_0}$ a visible action, as additionally:\\
@@
  =&\!\!
-{\bigoplus_{\substack{i=0\\j_0\in J_{1i}}}^{m_1}\!\!\!
-\vis{{\beta_{1ij_0}}\subst{\!\bigodot_{k=i-1}^{0} \!\!\!\!\Post_{1k} } }  \,\oplus\, \vis{{\beta_{2j_0}}\subst{\!\bigodot_{k=m_1}^{0}\!\!\!\Post_{1k}}}}\oplus\!
+{\bigoplus_{\substack{i=1\\j_0\in J_{1i}}}^{m_1}\!\!\!
+\vis{{\beta_{1ij_0}}\subst{\!\bigodot_{k=i-1}^{1} \!\!\!\!\Post_{1k} } }  \,\oplus\, \vis{{\beta_{2j_0}}\subst{\!\bigodot_{k=m_1}^{1}\!\!\!\Post_{1k}}}}\oplus\!
 \\
 &\qquad\qquad
-{ \!\bigoplus_{\substack{i=0\\j_0\in J_{3i}}}^{m_2}\!\! \vis{{\beta_{3ij_0}} \subst{\!\bigodot_{k=i-1}^{0}\!\!\!\Post_{3k}\shortodot\Post_2\shortodot
-\!\!\bigodot_{k=m_1}^{0}\!\!\!\Post_{1k}}}}
+{ \!\bigoplus_{\substack{i=0\\j_0\in J_{3i}}}^{m_2}\!\! \vis{{\beta_{3ij_0}} \subst{\!\bigodot_{k=i-1}^{1}\!\!\!\Post_{3k}\shortodot\Post_2\shortodot
+\!\!\bigodot_{k=m_1}^{1}\!\!\!\Post_{1k}}}}
 \end{align*}}
@@
 \noindent We have, by definition of $n_i$ and $n'_i$:\\
-$\displaystyle{\forall{i\in[0\,..\,m\!-\!1]}, \beta_{1 n_i j_0}\subst{\bigodot_{k=n_i-1}^{0}\Post_{1k}}=\beta_i}$, \qquad$\displaystyle{\beta_{2 j_0}\subst{\bigodot_{k=m_1}^{0} \Post_{1k} }=\beta_m}$, and \\
-$\displaystyle{\forall{i\in[m\!+\!1\,..\,n]}, \beta_{3 n_i' j_0}\subst{\bigodot_{k=n_i'-1}^{0}\Post_{3k}\shortodot\Post_2\shortodot\bigodot_{k=m_1}^{0}\Post_{1k}}=\beta_i}$\\
+$\displaystyle{\forall{i\in[1\,..\,m\!-\!1]}, \beta_{1 n_i j_0}\subst{\bigodot_{k=n_i-1}^{1}\Post_{1k}}=\beta_i}$, \qquad$\displaystyle{\beta_{2 j_0}\subst{\bigodot_{k=m_1}^{1} \Post_{1k} }=\beta_m}$, and \\
+$\displaystyle{\forall{i\in[m\!+\!1\,..\,n]}, \beta_{3 n_i' j_0}\subst{\bigodot_{k=n_i'-1}^{1}\Post_{3k}\shortodot\Post_2\shortodot\bigodot_{k=m_1}^{1}\Post_{1k}}=\beta_i}$\\
 
@@
 \begin{enumerate}
-\item For the first $\tau$ OTs, i.e. $p\in [0\,..\,m_1]$. We have: \\
+\item For the first $\tau$ OTs, i.e. $p\in [1\,..\,m_1]$. We have: \\
 Either there is $i$ such that $p=n_i$, and thus $\beta_i$ and $\beta_{1 p j_0}$ are defined. In this case by Lemma~\ref{lem-Weakcompose1},  we have: 
@@
          {	\set{\gamma'_2},\Pred\,'_2,\Post\,'_2 }
-         {\ostate{{(s_{20j})}^{j\in L}\uplus (s_{mj})^{j\in L_Q}}\OTWeakarrow {\alpha'} \ostate{{(s_{21j})}^{j\in L}\uplus (s_{(m+1)j})^{j\in L_Q}}}\]
+         {\ostate{{(s_{21j})}^{j\in L}\uplus (s_{mj})^{j\in L_Q}}\OTWeakarrow {\alpha'} \ostate{{(s_{22j})}^{j\in L}\uplus (s_{(m+1)j})^{j\in L_Q}}}\]
 with
@@
 
-\item For the last $\tau$ OTs, i.e. $p\in [0\,..\,m_2]$. We have similarly to the first case:\\
+\item For the last $\tau$ OTs, i.e. $p\in [1\,..\,m_2]$. We have similarly to the first case:\\
  Either there is $i$ such that $p=n'_i$, and thus $\beta_i$ and $\beta_{1 p j_0}$ are defined. In this case by Lemma~\ref{lem-Weakcompose1}, we have: 
@@
 \begin{align*}
-\alpha''=&\alpha'{\subst{\bigodot_{j=m_1}^{0}\Post'_{1j}}}\\
+\alpha''=&\alpha'{\subst{\bigodot_{j=m_1}^{1}\Post'_{1j}}}\\
 \set{\gamma'}=&
- \bigoplus_{i=0}^{m_1}\set{\gamma'_{1i}}\subst{\bigodot_{k=i-1}^{0}\Post\,'_{1k}}\,\oplus\,
-\set{\gamma'_{2}}\subst{\bigodot_{k=m_1}^{0}\Post\,'_{1k}}\,\oplus\\&\qquad
- \bigoplus_{i=0}^{m_2}\set{\gamma'_{3i}}\subst{\bigodot_{k=i-1}^{0}\Post\,'_{3k}\shortodot\Post\,'_2\shortodot\bigodot_{k=n}^{0}\Post\,'_{1k}}
+ \bigoplus_{i=1}^{m_1}\set{\gamma'_{1i}}\subst{\bigodot_{k=i-1}^{1}\Post\,'_{1k}}\,\oplus\,
+\set{\gamma'_{2}}\subst{\bigodot_{k=m_1}^{1}\Post\,'_{1k}}\,\oplus\\&\qquad
+ \bigoplus_{i=1}^{m_2}\set{\gamma'_{3i}}\subst{\bigodot_{k=i-1}^{1}\Post\,'_{3k}\shortodot\Post\,'_2\shortodot\bigodot_{k=n}^{1}\Post\,'_{1k}}
 \displaybreak[0]\\
-\Pred\,''=&\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigodot_{j=i-1}^{0}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigodot_{j=m_1}^{0}\Post\,'_{1j}}\land\\ 
-&\qquad\bigwedge_{i=0}^{m_2}\Pred\,'_{3i}\subst{\bigodot_{j=i-1}^{0}\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_2}^{0}\Post\,'_{1j}}\displaybreak[0]\\
-\Post\,''=&\bigodot_{j=m_2}^{0}\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{0}\Post\,'_{1j}
+\Pred\,''=&\bigwedge_{i=1}^{m_1}\Pred\,'_{1i}\subst{\bigodot_{j=i-1}^{1}\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigodot_{j=m_1}^{1}\Post\,'_{1j}}\land\\ 
+&\qquad\bigwedge_{i=1}^{m_2}\Pred\,'_{3i}\subst{\bigodot_{j=i-1}^{1}\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_2}^{1}\Post\,'_{1j}}\displaybreak[0]\\
+\Post\,''=&\bigodot_{j=m_2}^{1}\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{1}\Post\,'_{1j}
 \end{align*}
@@
 {\small \begin{align*}
-\alpha''&=\alpha'\displaystyle{\subst{\bigodot_{j=m_1}^{0}\Post\,'_{1j}}}\\
-& = \alpha'\displaystyle{\subst{\bigodot_{j=m_1}^{0}\Post_{1j}}}&\text{$\alpha'$ only contains variables of $P$ untouched by $\Post_i$}\\
+\alpha''&=\alpha'\displaystyle{\subst{\bigodot_{j=m_1}^{1}\Post\,'_{1j}}}\\
+& = \alpha'\displaystyle{\subst{\bigodot_{j=m_1}^{1}\Post_{1j}}}&\text{$\alpha'$ only contains variables of $P$ untouched by $\Post_i$}\\
 & = \alpha
@@
 {\small \begin{equation*}
-\begin{split}\gamma'_j=&\bigoplus_{i=0}^{m_1} \vis{{\beta_{1ij}}\subst{\bigodot_{k=i-1}^{0}\! \Post_{1k} } }  \oplus  \vis{{\beta_{2j}}\subst{\bigodot_{k=m_1}^{0}\!\Post_{1k}}}\, \oplus\\&
-\bigoplus_{i=0}^{m_2} \vis{\beta_{3ij} \subst{\!\bigodot_{k=i-1}^{0}\!\!\!\Post_{3k}\shortodot\Post_2\shortodot\bigodot_{k=m_1}^{0}\!\!\Post_{1k}}}
+\begin{split}\gamma'_j=&\bigoplus_{i=1}^{m_1} \vis{{\beta_{1ij}}\subst{\bigodot_{k=i-1}^{1}\! \Post_{1k} } }  \oplus  \vis{{\beta_{2j}}\subst{\bigodot_{k=m_1}^{1}\!\Post_{1k}}}\, \oplus\\&
+\bigoplus_{i=1}^{m_2} \vis{\beta_{3ij} \subst{\!\bigodot_{k=i-1}^{1}\!\!\!\Post_{3k}\shortodot\Post_2\shortodot\bigodot_{k=m_1}^{1}\!\!\Post_{1k}}}
 \end{split}
@@
 \gamma'_j =&
-\bigoplus_{i=0}^{m_1}{\gamma'_{1ij}}\subst{\bigodot_{k=i-1}^{0}\Post\,'_{1k}}\oplus
- {\gamma'_{2 j}}\subst{\bigodot_{k=m_1}^{0}\Post\,'_{1k}}\,\oplus\\&\quad \bigoplus_{i=0}^{m_2}{\gamma'_{3ij}}\subst{\bigodot_{k=i-1}^{0}\Post\,'_{3k}\shortodot\Post\,'_2\shortodot\bigodot_{k=n}^{0}\Post\,'_{1k}}\\
+\bigoplus_{i=1}^{m_1}{\gamma'_{1ij}}\subst{\bigodot_{k=i-1}^{1}\Post\,'_{1k}}\oplus
+ {\gamma'_{2 j}}\subst{\bigodot_{k=m_1}^{1}\Post\,'_{1k}}\,\oplus\\&\quad \bigoplus_{i=1}^{m_2}{\gamma'_{3ij}}\subst{\bigodot_{k=i-1}^{1}\Post\,'_{3k}\shortodot\Post\,'_2\shortodot\bigodot_{k=n}^{1}\Post\,'_{1k}}\\
 =&
-{\bigoplus_{t=0}^{n} {\gamma_{tj}}\subst{\bigodot_{k=t-1}^{0} \Post_{k}}}   
+{\bigoplus_{t=1}^{n} {\gamma_{tj}}\subst{\bigodot_{k=t-1}^{1} \Post_{k}}}   
 \end{split}
@@
 \begin{align*}
-\Pred\,''&=\Big(\bigwedge_{i=0}^{m_1}\Pred\,'_{1i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}}\\ &\qquad\qquad \land
+\Pred\,''&=\Big(\bigwedge_{i=1}^{m_1}\Pred\,'_{1i}\subst{\bigodot_{j=i-1}^{1}\!\!\Post\,'_{1j}}\land\Pred\,'_2 \subst{\bigodot_{j=m_1}^{1}\!\!\Post\,'_{1j}}\\ &\qquad\qquad \land
 %~\quad
-\bigwedge_{i=0}^{m_3}\Pred\,'_{3i}\subst{\bigodot_{j=i-1}^{0}\!\!\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{0}\!\Post\,'_{1j}}\Big)\\
-&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\!\!\bigodot_{j=p-1}^{0}\!\!\Post_{1j}}\land\Pred_2\subst{\!\!\bigodot_{p=m_1}^{0}\!\!\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\!\bigodot_{j=p-1}^{0}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\!\bigodot_{p=m_1}^{0}\!\!\Post_{1p}}\Big)\\&\qquad
-\land \bigwedge_{t=0}^{n} \Pred_t\bigodot_{i=t-1}^{0}\!\!\Post_i%\\&\qquad
-\land \Big( \bigwedge_{i=0}^{m-1}(\beta_{1{n_i}{j_0}}=\alpha_i)\subst{\bigodot_{j={n_i}-1}^{0}\Post\,'_{1j}}\land(\beta_{2{j_0}}=\alpha_m) \subst{\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}}\\ &\qquad
-~\quad\land\bigwedge_{i=m+1}^{n}(\beta_{3{n'_i}{j_0}}=\alpha_i)\subst{\bigodot_{j=n'_i-1}^{0}\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{0}\!\!\Post\,'_{1j}}\Big)\displaybreak[0]\\
-&=\Big(\bigwedge_{p=0}^{m_1}\!\Pred_{1p}\subst{\!\!\bigodot_{j=p-1}^{0}\!\!\Post_{1j}}\big)\land\Pred_2\subst{\!\!\bigodot_{p=m_1}^{0}\!\!\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\!\!\bigodot_{j=p-1}^{0}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\!\bigodot_{p=m_1}^{0}\!\!\Post_{1p}}\Big)\\&\qquad
-\land \bigwedge_{t=0}^{n} \Pred_t\bigodot_{i=t-1}^{0}\!\!\Post_i
-\land \Big(\bigwedge_{i=0}^{m-1}(\beta_{i}=\alpha_i)\subst{\bigodot_{j={i-1}}^{0}\!\!\Post_{j}}\land(\beta_m=\alpha_m )\subst{\bigodot_{j=m}^{0}\Post_{j}}\\ &\qquad
-~\quad\land\bigwedge_{i=m+1}^{n}(\beta_i=\alpha_i)\subst{\bigodot_{j=i-1}^{m}\!\!\Post_j\shortodot\Post_m\shortodot\bigodot_{j=m-1}^{0}\!\!\Post_{j}}\Big)\\
+\bigwedge_{i=1}^{m_3}\Pred\,'_{3i}\subst{\bigodot_{j=i-1}^{1}\!\!\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{1}\!\Post\,'_{1j}}\Big)\\
+&=\Big(\bigwedge_{p=1}^{m_1}\!\Pred_{1p}\subst{\!\!\bigodot_{j=p-1}^{1}\!\!\Post_{1j}}\land\Pred_2\subst{\!\bigodot_{p=m_1}^{1}\!\!\Post_{1p}}\land\!
+\bigwedge_{p=1}^{m_2}\!\Pred_{3p}\subst{\!\!\bigodot_{j=p-1}^{1}\!\!\Post_{3j}\otimes\Post_2 \otimes\!\!\bigodot_{p=m_1}^{1}\!\!\Post_{1p}}\Big)\\&\qquad
+\land \bigwedge_{t=1}^{n} \Pred_t\bigodot_{i=t-1}^{1}\!\!\Post_i%\\&\qquad
+\land \Big( \bigwedge_{i=1}^{m-1}(\beta_{1{n_i}{j_0}}=\alpha_i)\subst{\bigodot_{j={n_i}-1}^{1}\Post\,'_{1j}}\land(\beta_{2{j_0}}=\alpha_m) \subst{\bigodot_{j=m_1}^{1}\!\!\Post\,'_{1j}}\\ &\qquad
+~\quad\land\bigwedge_{i=m+1}^{n}(\beta_{3{n'_i}{j_0}}=\alpha_i)\subst{\bigodot_{j=n'_i-1}^{1}\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{1}\!\!\Post\,'_{1j}}\Big)\displaybreak[0]\\
+&=\Big(\bigwedge_{p=1}^{m_1}\!\Pred_{1p}\subst{\!\!\bigodot_{j=p-1}^{1}\!\!\Post_{1j}}\big)\land\Pred_2\subst{\!\bigodot_{p=m_1}^{1}\!\!\Post_{1p}}\land\!
+\bigwedge_{p=1}^{m_2}\!\Pred_{3p}\subst{\!\!\bigodot_{j=p-1}^{1}\!\!\Post_{3j}\!\otimes\!\Post_2\!
+\otimes\!\!\bigodot_{p=m_1}^{1}\!\!\Post_{1p}}\Big)\\&\qquad
+\land \bigwedge_{t=1}^{n} \Pred_t\bigodot_{i=t-1}^{1}\!\!\Post_i
+\land \Big(\bigwedge_{i=1}^{m-1}(\beta_{i}=\alpha_i)\subst{\bigodot_{j={i-1}}^{1}\!\!\Post_{j}}\land(\beta_m=\alpha_m )\subst{\bigodot_{j=m}^{1}\Post_{j}}\\ &\qquad
+~\quad\land\bigwedge_{i=m+1}^{n}(\beta_i=\alpha_i)\subst{\bigodot_{j=i-1}^{m}\!\!\Post_j\shortodot\Post_m\shortodot\bigodot_{j=m-1}^{1}\!\!\Post_{j}}\Big)\\
 &=\Pred
@@
 \begin{split}
-\Post\,''&=\bigodot_{j=m_2}^{0}\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{0}\Post\,'_{1j}\\
-&=\left(\bigodot_{j=m_2}^{0}\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{0}\Post\,'_{1j}\right)\uplus \bigodot_{j=n}^{0}\Post_j\\
-&=\Post \uplus \bigodot_{j=n}^{0}\Post_j\
+\Post\,''&=\bigodot_{j=m_2}^{1}\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{1}\Post\,'_{1j}\\
+&=\left(\bigodot_{j=m_2}^{1}\Post\,'_{3j}\shortodot\Post\,'_2\shortodot\bigodot_{j=m_1}^{1}\Post\,'_{1j}\right)\uplus \bigodot_{j=n}^{1}\Post_j\\
+&=\Post \uplus \bigodot_{j=n}^{1}\Post_j\
 \end{split}

### 2022-10-19 2016-Weak-FH-Bisim/JLAMP-AnswerToReviewers.tex
lettre premiere partie

@@
 
-\medskip
+After this, we will review in the next pages the comments of the reviewers and explain how we addressed them.
 
-%After this, we will review in the next pages the comments of the reviewers and explain how we addressed them.
+The major improvements we performed are the following:
+\begin{itemize}
+\item We added numerous comparison with related works as suggested (mostly by reviewer 1). 
+Most of this positioning has been added to Section 6 ``Related works''. 
+We also added a few precise comparisons in the text but we felt it was sometimes too  early, some of them are just forward references to the Section 6 at the points where the knowledgeable reader would expect a comparison with related works.
+\item We tried to address the comments of both reviewer requiring n early simple example; in practice we moved in Section  2.2 the definition of the choice operator in pNets, and added informal explanations on the definition of pNets before the formal definitions.
+\item We are particularly grateful to the reviewer for highlighting the fact that we misused bisimilarity relatively to bisimulation.
+We corrected this point and checked thoroughly in the paper that we used the right notion at the right place.
+\end{itemize}
+
+We thank again the reviewer for their comments and believe the new version of our article  is much better.
+
+\begin{flushright}
+  Best Regards,\\
+  Rab\'ea Ameur-Boulifa, Ludovic Henrio, and Eric Madelaine
+\end{flushright}
+
+\newpage
 
@@
 bla
-
-\newpage
 
@@
 
-\begin{flushright}
-  Best Regards,\\
-  Rab\'ea Ameur-Boulifa, Ludovic Henrio, and Eric Madelaine
-\end{flushright}
 \end{document}

### 2022-10-19 2016-Weak-FH-Bisim/JLAMP-AnswerToReviewers.tex

@@
 
+As explained above, we quote below and reply to text requiring changes that we did not  address in a straightforward manner.
+We additionally produced a version of the paper highlighting all the changes we made.
+
 We thank again the reviewer for their comments and believe the new version of our article  is much better.
@@
 \section*{Response to reviewer 1}
+\begin{review}
+Reviewer \#1: Synopsis
+
+The article under review presents under one roof work done by some of its authors (and others) over the years on the study of pNets and open pNets as well as on notions of bisimilarity over those models and their compositionality properties.
+In previous work, the authors proposed pNets as a hierarchical model for describing large concurrent systems and their specifications, studied notions of behavioural equivalence over pNets, provided some tool support for that model and applied it to case studies.
+
+The aim of this article is to present and study the foundational theory of open pNets, namely pNets with holes at some of their leaves, which can be instantiated when refining the resulting system specification.
+The article develops the semantics of open pNets via translation to open automata, namely LTSs with parameters and holes.
+It also develops a behavioural theory for open automata (and thus open pNets) adapting de Simone's FH-bisimilarity to that notion of automaton and showing congruence properties for the resulting strong and weak notions of bisimilarity.
+In particular, the authors identify sufficient conditions guaranteeing the compositionality of strong and weak bisimulation equivalence.
+The technical contributions are illustrated throughout with a running example that describes a transport protocol.
+
+Evaluation
+
+I enjoyed reading the paper somewhat and appreciate the long-term effort by the authors and their co-workers on using variations on time-honoured models and techniques from process algebra and concurrency theory to good effect in modelling and verification of non-trivial systems.
+The authors have also done some valuable tool development accompanying their theoretical work.
+In particular, I am not aware of other uses of FH-bisimulation-like equivalences in practice.
+
+The technical developments in the paper seem, by and large, sound to me.
+However, as the authors can see from the annotated scan of their paper that accompanies this short textual review, there is still some work that needs to be done in order to iron out some (relatively minor) remaining issues.
+Moreover, even though the presentation is reasonably clear, it should still be improved, polished and clarified in places.
+Last, but not least, it seems to me that several of the notions presented by the authors have connections with classic ones in the literature.
+I feel that the paper would improve substantially if the authors compared some of their contributions more carefully with the ones I point out in the annotated scan.
+\end{review}
+Thank you for the references; we believe we added all of them at some point
 
 \begin{review}
-blabla de la review
+For instance, a reader might ask: Why should I use open pNets instead of the mature mCRL2 tool set, which seems to support many of the features open pNets offer?
+(Note: I am not claiming that mCRL2 and its modelling language offer everything that open pNets
+do. I am asking the authors to discuss their work vis-a-vis existing models and tools more thoroughly.) 
 \end{review}
-Answer
+We agree that such comparisons were missing and we compared our approach to mCRL2 and some other approaches (see Section 6).
+We did not insist much on the comparison of the tools as the focus of the article is mostly theoretical, but we believe that, while mCRL2 tools are more stable and user-ready, the general approach we provide for reasoning on composition of systems could be adapted to extend composition and decomposition results on frameworks like mCRL2, this is why we also cite recent results on the decomposition of mCRL2 processes.
+A deeper comparison with mCRL2constructs  would also be possible of course but we were afraid it would get lengthy and less focused on the main contribution of the paper.
 
 \begin{review}
-suite
+What are the relationships with context systems and context-dependent bisimilarity as defined by Larsen and colleagues?
+Could you compare your model with other hierarchical models of concurrent systems and the verification techniques they support?
 \end{review}
-bla
+We also added several points of comparison with the works of Larsen and colleagues
 
-As explained above, we quote below and reply to text requiring changes that we did not  address in a straightforward manner.
-We additionally produced a version of the paper highlighting all the changes we made: \TODO{Si tu arrives a produire le latexdiff} \url{url???}
+\begin{review}
 
-\ERIC{P4, *say that this is like in Symbolic Bisimulation}
-\begin{quote}Pas sur du tout, je bosse encore la-dessus...
-\end{quote}
+In summary, I think that the paper offers a good contribution, but that a revision addressing the comments raised in the annotated scan accompanying this review and the above general comments is needed before the paper can be accepted.
 
-\ERIC{P4, *Any relations with the conditions on SOS rule formats guaranteeing compositionality of weak bisimilarity?}
-\begin{quote} 
-\TODO{L'ajout est dans l'introduction pargra. avant la structure}
-non je n'ai pas repondu ici... voir paragraph page precedente, est-ce suffisant "
-\end{quote}
+\emph{The rest of the review was provided as a pdf, we only mention a few of the points we treated, all comments have been addressed.}
+\end{review}
 
-\ERIC{P14, *Is your definition a combination of De Simone FH-bisimulation and Hennessy and Lin's symbolic bisimulation?}
-\begin{quote}
-\TODO{L'ajout est dans la section 3.2, fin pargraph 1}
-Je n'ai pas redige ca... mais l'idee pourrait etre que en gros oui, et en y ajoutant le formalisme synch vecteurs de Arnold et Nivat, 
-mais que notre approache est sensiblement differente, puisque plus syntaxique, pour permettre le developpement de representation finies, d'algorithmes, et d'outils...
-\end{quote}
+\begin{review}
+P4 *say that this is like in Symbolic Bisimulation
+\end{review}
+Yes this is similar. We added a note.
 
-\ERIC{P17, *What is the comoplexity of this "brute force approach"?}
-\begin{quote}
-le paragraph existant etait difficilement comprehensible et loin de notre implementation dans l'outil. J'ai remplace par quelque chose de plus factuel:
-"The definition of this predicate is not constructive.
-In our tool [39], we construct a logical formula encoding the matching and unification conditions involved, and let an SMT engine (in the current implementation Z3 [30]) decide its satisfiability"
-\end{quote}
+\begin{review}
+P4, *Any relations with the conditions on SOS rule formats guaranteeing compositionality of weak bisimilarity?
+\end{review}
+ The relation here is quite far, because our rules are not structural in the sense of SOS operators. We added a remark to make this clear, in the previous page.
 
-\ERIC{page 36, *It'd be a good idea to give links to software tools implementing your approach and to examples case-studies}
-\begin{quote}
-\TODO{L'ajout est dans la conclusion [30,31]...}
+\begin{review}
+P14, *Is your definition a combination of De Simone FH-bisimulation and Hennessy and Lin's symbolic bisimulation?
+\end{review}
+Yes. We added a sentence to make this explicit.
 
-J'ai ajoute 7 ligns ici: "In this platform [...] different encodings of operators".
-C'est un peu faible parceque 1) les outils de sont pas encore accessibles en ligne (ca aurait du etre l'achevement du stage de Slava...), et 2) on n'a pas de papier sur un vrai "use-case', a part le AVOCS sur le satellite, mais qui ne fait pas de bisimulation, juste des proprietes temporelles.
-\end{quote}
+\begin{review}
+{P17, *What is the complexity of this "brute force approach"?}
+\end{review}
+We changed this paragraph to make it more concrete and related to our implementation.
+
+\begin{review}
+{P17, *Are these related to some of the constructs on rule format for weak bisimilarity"?}
+\end{review}
+Somehow. We answered this in page 5.
+
+\begin{review}
+{page 36, *It'd be a good idea to give links to software tools implementing your approach and to examples case-studies}
+\end{review}
+In the first paragraph of the conclusion, we added citations to papers describing our tools ans case-studies.
 

### 2022-10-19 2016-Weak-FH-Bisim/JLAMP-AnswerToReviewers.tex
review 1

@@
 We also added a few precise comparisons in the text but we felt it was sometimes too  early, some of them are just forward references to the Section 6 at the points where the knowledgeable reader would expect a comparison with related works.
+Therse references include works by Larsen, quotienting techniques, mCRL2, contextual equivalence, more comparison with GSOS, works of de Simone and symbolic bisimulation, and others.
 \item We tried to address the comments of both reviewer requiring n early simple example; in practice we moved in Section  2.2 the definition of the choice operator in pNets, and added informal explanations on the definition of pNets before the formal definitions.
+We also gathered arguments around observability and choice in a single example as it was a bit confusing.
 \item We are particularly grateful to the reviewer for highlighting the fact that we misused bisimilarity relatively to bisimulation.
@@
 \begin{review}
+P2: can you speculate for the lack of applications ...
+\end{review}
+Done briefly (not sure long speculation would be much useful but a short hint clearly helps.
+
+\begin{review}
 P4 *say that this is like in Symbolic Bisimulation
@@
  The relation here is quite far, because our rules are not structural in the sense of SOS operators. We added a remark to make this clear, in the previous page.
+
+\begin{review}
+P5: many sorted setting 
+\end{review}
+we did not mention many-sorted logic as we are not sure it helps a lot here and it might confuse the reader because we already use sorts (for some kind of interface signatures made of actions).
+Instead we added a footnote about the different kind of terms both in the paper and in the tools.
+
+\begin{review}
+P8: Vars(P) defined too late
+\end{review}
+We indeed have two mutually dependent definitions, this is merely a problem of presentation of two long definitions, we added an informal definition ans a forward reference.
+
+\begin{review}
+P10: can you be sure that your theory ``conservatively extends'' ...
+\end{review}
+No, in the sense that the proof would be long, easy, only partial by nature (closed vs open systems) and not publishable. We added one sentence here however to clarify things.
 
@@
 
+\begin{review}
+Reviewer \#2: SUMMARY
+
+The paper studies bisimulation equivalences for open systems, here represented by hierarchically structured systems with placeholders, called open pNets.
+Open pNets are tree-like structures that combine fully specified parameterized labelled transition systems (pLTS) and some unknown
+components represented as (sorted) holes. Here a pLTS is defined by a set of guarded transitions between states together
+with variables assignment. Notably, open pNets can be (de)composed by filling their holes with other pNets.
+Bisimulation equivalences for open pNets are obtained by introducing open automata as their semantic model:
+open transitions in open automata carry some sort of guarded action labels that allow to require some properties about the
+behaviour of placeholders and to fix some variables assignment.
+First, a notion of strong bisimulation is defined, whose key feature is the possibility to simulate a single open transition
+with a set of open transitions. Such bisimulation is called FH-bisimulation after the Formal Hypotheses it imposes
+on the unknown components of the system. The key property is that the equivalence induced by FH-bisimulation
+is a congruence w.r.t. the composition of open pNets (Th.5, composability).
+Second, weak bisimulation is also defined by taking silent actions into account.
+Note that the definition of weak transitions is here more involved than usual due to the rich structure of labels.
+Under the hypothesis of non-observability of silent actions (Def.11), the congruence result is also extended
+to weak FH-bisimilarity. Although this may look surprising, Def.11 is tailored to avoid the usual counterexamples
+that arise in process algebra-like frameworks.
+A running example of a simple message transport protocol specification vs implementation (adapted from the literature) is used
+to illustrate the key definitions and the main findings.
+Related work is extensively discussed in Section 6.
+
+EVALUATION
+
+The problem addressed in the paper (bisimulation for open systems) is interesting
+and worth investigation. It falls well in the scope of the journal.
+The framework of open pNets is semantically rich but technically heavy, so the notation is quite complicated to follow
+in several places. Even the small-sized running example gives rise to complex figures and annotations.
+This is due to the presence of actions, guards and assignments in a single label, together with the
+need to coordinate the transitions of placeholders by means of synchronisation vectors.
+Another limitation is that the structure of the modelled system looks quite static, e.g. holes are used
+in a linear manner (cannot be created, duplicated or deleted).
+As a coarse grain analogy, the definition of open pNets resembles the notion of "context" in a process
+algebraic setting, that is a partial composition of operators whose semantics is defined by (SOS) inference
+rules in some format that guarantees the linear usage of holes throughout the computation.
+Certainly here the analogy is complicated by the presence of variables, (symbolic) guards and assignments,
+and by the fact that ad hoc compositions can be considered (as opposed to having a fixed set of operators
+as in the case of process algebras).
+
+I wonder if an incremental presentation (e.g. briefly discussing the case of open pNets without variables first)
+could improve the readability.
+-> **~DONE ** we introduce a choice operator early on without presenting variables and formalism
+
+The main results are correct as far as I was able to check but not very surprising: their statements are
+complicated by the complexity of the chosen framework, but the properties agree with intuition.
+The most ingenious aspects are the possibility to simulate an open transition using many transitions,
+the composition of transitions and the definition of non-observability of silent actions.
+Sometimes it seems that the terms bisimulation and bisimilarity are used interchangeably, while
+this should not be the case (e.g., formally speaking we cannot say that bisimulation is an equivalence,
+because a FH-bisimulation is not necessarily so, while FH-bisimilarity is).
+-> ** DONE** we clarified this, thanks for pointing this out
+
+OTHER COMMENTS
+
+P5: Term algebra.. -> Term algebra.
+-> **DONE **
+
+P5: a set of action expressions \mathbb{E} called the action algebra -> a set of action expressions called the action algebra
+
+-> **DONE **
+
+P7, Def.1: give an example of a pLTS (even just a partially specified one).
+
+-> **DONE ** => Introduction de l'example 1 (CCS choice)
+
+P11,Fig.1: shouldn't the assignment that increments b_ec be associated with tau?
+
+-> **DONE ** Oui, the assignement of b_ec associated with tau => Figure retrvaillee
+
+P14,L-2: variablesverify -> variables verify
+
+-> **DONE **
+
+P15,Def.7: give an example of a transition that is (bi)simulated by many
+
+-> **DONE **
+
+P15,Th.1: FH-bisimulation is an equivalence -> FH-bisimilarity is an equivalence
+The statement must be changed accordingly: not any FH-bisimulation is an equivalence
+** DONE ** thanks for pointing this out
+
+P20,Fig.3: is SS_6 the same as SS_2? is SS_5 the same as SS_1? in SS_5, P-a -> p-a
+
+** DONE ** Correction de P-a dans  SS_5 (same as SS_1).
+
+P21,Def.10: justify the requirement that the predicate associated with the initial states is verifiable
+(e.g. why not requiring it to be a tautology?)
+-> is TRUE
+-> [Eric et Rabea] To be discussed 
+** Agree,  True is what is needed **
+
+** DONE ** Definition 10 modifie
+
+P24: "The condition J={j} is a bit restrictive ... " I disagree as you should be careful not to introduce sync of non observable actions
+** DONE **
+
+-> In fact, here we speak about the direction 2 in the definition.
+Having J={i,j} would ALLOW taus to occur synchronously but condition 1 still ensures that each process can do a tau separately.
+So yes we could introduce synchronized taus but as taus do not have to be synchronised it is not a problem.
+-> We added explanations at this point
+
+P24: the \cup with the dot inside is a weird symbol for concatenation
+-> [RABEA]
+** DONE *** Remplacement de \cup with dot par un autre symbole \oplus
+
+P26: Rule WT2 transforms each 3 ->  Rule WT2 transforms each 2 (?)
+-> [LUDO] check
+** DONE **
+
+P26: a sequence 3 WOTs -> a sequence of 3 WOTs
+** DONE **
+
+P29: but based on open automata -> but based on weak open automata
+
+** DONE ** 
+P30, Th.6: Weak FH-Bisimulation -> Weak FH-Bisimilarity
+the statement must be changed accordingly (check also Theorems 7-9)
+** DONE ** par Ludo?
+
+P33: are you considering state 202 or 000 in the example?
+-> [RABEA] check
+** DONE ** oui, ajout de precision
+
+P35: premisses -> premises (several times)
+** DONE **
+
+P35: an extension -> An extension
+** DONE **
+
+P37: missing reference []
+** DONE **
+
+P42, above (**): Pred_{p,u} -> Pred'_{p,u}
+-> [LUDO] check
+** DONE ** Oui
+
+P52,Lemma 4: having n=-1 and m=-1 in the base case is a bit strange. Can you rephrase the Lemma to link the base case to n=0,m=0?
+\end{review}
+
 \end{document}

### 2022-10-19 2016-Weak-FH-Bisim/JLAMP-AnswerToReviewers.tex
fiorst versin of letter

@@
 could improve the readability.
--> **~DONE ** we introduce a choice operator early on without presenting variables and formalism
+\end{review}
+We introduce a choice operator early on without presenting aspects on variables and before the formalisation.
 
+\begin{review}
 The main results are correct as far as I was able to check but not very surprising: their statements are
@@
 because a FH-bisimulation is not necessarily so, while FH-bisimilarity is).
--> ** DONE** we clarified this, thanks for pointing this out
+\end{review}
+We clarified this, thanks for pointing this out
 
+\begin{review}
 OTHER COMMENTS
 
-P5: Term algebra.. -> Term algebra.
--> **DONE **
-
-P5: a set of action expressions \mathbb{E} called the action algebra -> a set of action expressions called the action algebra
-
--> **DONE **
+...
 
 P7, Def.1: give an example of a pLTS (even just a partially specified one).
+\end{review}
+We now have the choice operator with a pLTS before
 
--> **DONE ** => Introduction de l'example 1 (CCS choice)
-
-P11,Fig.1: shouldn't the assignment that increments b_ec be associated with tau?
-
--> **DONE ** Oui, the assignement of b_ec associated with tau => Figure retrvaillee
-
-P14,L-2: variablesverify -> variables verify
-
--> **DONE **
+\begin{review}
+\ldots
 
 P15,Def.7: give an example of a transition that is (bi)simulated by many
+\end{review}
 
--> **DONE **
-
+We added this, in a partial automaton though to avoid a lengthy example here
+\begin{review}
 P15,Th.1: FH-bisimulation is an equivalence -> FH-bisimilarity is an equivalence
 The statement must be changed accordingly: not any FH-bisimulation is an equivalence
-** DONE ** thanks for pointing this out
+\end{review}
+Done, see maini part of the letter; thanks for pointing this out
 
-P20,Fig.3: is SS_6 the same as SS_2? is SS_5 the same as SS_1? in SS_5, P-a -> p-a
-
-** DONE ** Correction de P-a dans  SS_5 (same as SS_1).
-
-P21,Def.10: justify the requirement that the predicate associated with the initial states is verifiable
-(e.g. why not requiring it to be a tautology?)
--> is TRUE
--> [Eric et Rabea] To be discussed 
-** Agree,  True is what is needed **
-
-** DONE ** Definition 10 modifie
+\begin{review}
+\ldots
 
 P24: "The condition J={j} is a bit restrictive ... " I disagree as you should be careful not to introduce sync of non observable actions
-** DONE **
-
--> In fact, here we speak about the direction 2 in the definition.
+\end{review}
+ In fact, here we speak about the direction 2 in the definition.
 Having J={i,j} would ALLOW taus to occur synchronously but condition 1 still ensures that each process can do a tau separately.
 So yes we could introduce synchronized taus but as taus do not have to be synchronised it is not a problem.
--> We added explanations at this point
+We added explanations at this point, our text was indeed imprecise.
 
-P24: the \cup with the dot inside is a weird symbol for concatenation
--> [RABEA]
-** DONE *** Remplacement de \cup with dot par un autre symbole \oplus
+\begin{review}
 
-P26: Rule WT2 transforms each 3 ->  Rule WT2 transforms each 2 (?)
--> [LUDO] check
-** DONE **
+P24: the $\cup$ with the dot inside is a weird symbol for concatenation
 
-P26: a sequence 3 WOTs -> a sequence of 3 WOTs
-** DONE **
+\end{review}
+We chose a union operator as it is a pointwise concatenation so it also does a union on disjoint indexed sets for example ... but this was probably too intricate here.
 
-P29: but based on open automata -> but based on weak open automata
+We tried \texttt{oplus}, we hope it makes more sense.
 
-** DONE ** 
-P30, Th.6: Weak FH-Bisimulation -> Weak FH-Bisimilarity
-the statement must be changed accordingly (check also Theorems 7-9)
-** DONE ** par Ludo?
-
-P33: are you considering state 202 or 000 in the example?
--> [RABEA] check
-** DONE ** oui, ajout de precision
-
-P35: premisses -> premises (several times)
-** DONE **
-
-P35: an extension -> An extension
-** DONE **
-
-P37: missing reference []
-** DONE **
-
-P42, above (**): Pred_{p,u} -> Pred'_{p,u}
--> [LUDO] check
-** DONE ** Oui
+\begin{review}
+\ldots
 
@@
 \end{review}
+We did this, but this required a lot of changes and many $1$ instead of $0$ in the rest of the proofs/theorems, to be consistent.
 

### 2022-10-20 2016-Weak-FH-Bisim/JLAMP-AnswerToReviewers.tex
rev 2 title
mise en page

@@
 \usepackage[latin1]{inputenc} 
-\usepackage{alltt,url}
+\usepackage{alltt,url,pdfpages}
 %% Old ttbox definition without frame:
@@
 As explained above, we quote below and reply to text requiring changes that we did not  address in a straightforward manner.
-We additionally produced a version of the paper highlighting all the changes we made.
+We additionally produced a version of the body of the  paper highlighting all the changes we made.
 
@@
 \end{review}
-Thank you for the references; we believe we added all of them at some point
+Thank you for the references;  we added  them at some point
 
@@
 In the first paragraph of the conclusion, we added citations to papers describing our tools ans case-studies.
+
+\section*{Response to reviewer 2}
 
@@
 
+\includepdf[pages=-]{WeakBisim-diff.pdf}
+
 \end{document}

### 2022-10-20 2016-Weak-FH-Bisim/WeakBisim.tex
mise en page

@@
 
-Beware that even if open transitions may look similar to the notion of Transition System Specification \cite{GROOTE1992202,GROOTE20063} and other forms of SOS rules, they are \emph{not} structural rules, but rules defining the behaviour of the global states of the system.
+Note that even if open transitions  look similar to the notion of Transition System Specification \cite{GROOTE1992202,GROOTE20063} and other forms of SOS rules, they are \emph{not} structural rules, but rules defining the behaviour of the global states of the system.
 
@@
 \item A resulting weak FH-bisimilarity equivalence for open pNets and a simple static condition on synchronisation vectors inside pNets that is sufficient to ensure that weak FH-bisimilarity is compositional.
-\item An illustrative example based on a simple transport protocol, showing the construction of the weak open transitions, and the proof of weak FH-bisimulation.
+\item An illustrative example based on a  transport protocol, showing the construction of the weak open transitions, and the proof of weak FH-bisimulation.
 \end{itemize}
@@
 
-This approach also allows us to specify a sufficient condition on allowed transitions to make weak bisimilarity compositional; namely it is not possible to synchronise on invisible actions from the holes or prevent them to occur.
+This approach also allows us to specify a sufficient condition on  transitions to make weak bisimilarity compositional; namely it is not possible to synchronise on invisible actions from the holes or prevent them to occur.
 This is loosely related to works on the syntactic conditions on SOS rules to check whether weak bisimulation is a congruence for some process algebra operators \cite{GROOTE1992202}.
@@
 indexed structures are always denoted with an exponent of the form $i\in I$.
-
 Consequently, $t_i^{i\in I}$ defines first $I$ the set over which the
@@
 set of \emph{synchronisation vectors} that express the possible
-synchronisation between the parameterised actions of a subset of the sub-trees.
-The pNets model is hierarchical in the structure of the processes, in contrast to the Statecharts formalism \cite{Harel:87}, which is widely used to model high-level behaviour,  that organises the states (but not processes) in a hierarchy.
-
-We introduce the notion of pNets through a simple example below, and define formally pLTSs and pNets afterwards:
+synchronisation between the  actions of a subset of the sub-trees.
+The pNets model is hierarchical in the structure of the processes, this contrasts with Statecharts  \cite{Harel:87} that model high-level behaviour by organising the states (but not processes) in a hierarchy.
+We introduce  pNets through a simple example below, and define formally pLTSs and pNets afterwards:
 
 \begin{example}[CCS choice]\label{ex:CCSplus}
-
 Here is the encoding of a choice operator.\\[1.5ex]
@@
 Each sub-pNet exposes
-a set of actions, called \emph{internal actions}. The synchronisation between global actions exposed by the pNet and
-internal actions of its sub-pNets is given by  \emph{synchronisation vectors}: a
-synchronisation vector synchronises one or several internal actions, and
+a set of actions, called \emph{internal actions}. \emph{Synchronisation vectors} define the synchronisation between global actions exposed by the pNet and
+internal actions of its sub-pNets: it synchronises one or several internal actions, and
 exposes a single resulting global action.
@@
 The proof of this theorem can be found in \ref{thm-equiv-proof}. The
-only non-trivial part of the proof is the proof of transitivity. It
+only non-trivial part of the proof is about transitivity. It
 relies on the following elements. First,  the transitive composition
@@
 
-This section defines the semantics of an open pNet via translation into an open automaton. 
+This section defines the semantics of an open pNet as a translation into an open automaton. 
 In this translation, the states of the open automaton are obtained as products of 
 the states of the pLTSs at the leaves of the composition. The
-predicates on the transitions are obtained both from the predicates on
+predicates on the transitions result both from the predicates on
 the transitions of the pLTSs, and from the synchronisation vectors involved in
@@
 $[a]$ denotes a sequence with a single element.
-
-As required actions are now sequences of observable actions, we need an operator to build them from set of actions that occur in open transitions, i.e.
+These new actions are sequences of observable actions, we thus need an operator to build them from a set of actions that occur in open transitions, i.e.
 an operator that takes a set of actions performed by one hole and produces a sequence of observable actions.
-
 Thus we define $\vis{\set\beta}$ as the mapping $\set\beta$  with only observable actions of the holes in $I$, but where each element is either empty or a list of length 1:
@@
 
-Compared to strong bisimulation, except the obvious use of weak open transitions to simulate an open transition, the condition on predicate is slightly changed concerning actions of the holes.
-Indeed only the visible actions of the holes must be compared and they form a list of actions, but of length at most one.
+Compared to strong bisimulation, except the  use of weak open transitions to simulate an open transition, the condition on predicate is slightly changed concerning actions of the holes.
+Indeed, only the visible actions of the holes must be compared and they form a list of actions, but of length at most one.
 
@@
 
-\begin{thm}[Weak FH-bisimilarity is an equivalence]\label{thm-weak-equiv} Weak FH-bisimilarity is 
+\begin{thm}[Weak FH-bisimilarity is an equivalence]\label{thm-weak-equiv} ~\\Weak FH-bisimilarity is 
 reflexive, symmetric and transitive.
@@
 Thus, even if we can define a weak FH-bisimilarity for CCS with $+$ it does not verify the necessary requirements for being a congruence.
-
 On the other side, the parallel operator defined similarly \emph{satisfies} Definition~\ref{def:non-obspNet}, and indeed bisimilarity is a congruence for the parallel operator in CCS.
@@
   \medskip
-  Now consider the relation $\mathcal{R}$ defined by the following triples:
-
-\noindent
+  Now consider the relation $\mathcal{R}$ defined by the triples in Table~\ref{fig:bisim-triples}.
+
+\begin{table}[tb]
   \begin{tabular}{|c|c|l|}
@@
     \end{tabular}
-
-  \medskip
+\caption{Bisimulation for the running example.}\label{fig:bisim-triples}
+\end{table}
+
   Checking that $\mathcal{R}$ is a weak FH-bisimulation means checking, for each of these triples, that each (strong) OT of one the states corresponds to a set of WOTs of the other, using the conditions from Definition \ref{def-Weak-bisim}.
@@
   \item Triple ($\text{b1},  100,  \texttt{b\_msg = s\_msg} \land \texttt{b\_ec = s\_ec}$) is in $\mathcal{R}$.
-  \item The verification condition \\
-    $\forall fv_{OT}.\, \{ \Pred \land \Pred_{OT}\\
-\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\!
-   \left[\exists fv_{OT_x}.
+  \item The verification condition 
+    \begin{multline*}
+\forall fv_{OT}.\, \{ \Pred \land \Pred_{OT}
+ \implies\!\!\! \bigvee_{x\in X}\!
+   \Big[\exists fv_{OT_x}.\\
   \left( \forall j\in J_x. \vis{\beta_j}\!=\!\gamma_{jx}\! \land\! \Pred_{OT_x}
      \!\land\! \alpha\!=\!\alpha_x\! \land\!  
-     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\!\Post_{OT_x}}\right)\right]\}}$
-
-\medskip Gives us:
+     \Pred_{s',t_x}\subst{\Post_{OT}\uplus\!\Post_{OT_x}}\right)\Big]\}
+\end{multline*}
+ gives us:
 
@@
 \begin{multline*}
-\Pred\,'_{p,u} \land \Pred_{OT_{p x}}\\
-       	\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}\!
+\Pred\,'_{p,u} \land \Pred_{OT_{p x}}
+       	 \implies\!\!\!\\ \bigvee_{y\in Y}\!
        	\Big( \forall j.\beta_{jpx}\!=\!\beta_{jpxy} \land\! \Pred_{OT_{pxy}}\!
        	\land\! \alpha_{px}\!=\!\alpha_{pxy} \!\land\!
-       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}\!\uplus\!\Post_{OT_{pxy}}}\Big)}
+       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}\!\uplus\!\Post_{OT_{pxy}}}\Big)
 \end{multline*}
@@
        	\begin{small}
-       		$\Pred_{s,u} \land \Pred_{OT}\\
-       		\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
+       		$\Pred_{s,u} \land \Pred_{OT} \implies\\
+       		\hspace{1cm} \!\!\! \displaystyle{\bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
        		\Big( \forall j. \beta_j=\beta_{jpxy}  \land \Pred_{OT_{pxy}}

### 2022-11-22 2016-Weak-FH-Bisim/WeakBisim.tex
corrections

@@
 method for these processes.
-Thirty years later,  no verification platform use this kind of approaches to provide proof methods for value-passing processes or open process expressions, perhaps because of the difficulty to apply these methods on industrial systems.
+Thirty years later,  no verification platform uses this kind of approaches to provide proof methods for value-passing processes or open process expressions, perhaps because of the difficulty to apply these methods on industrial systems.
 
@@
 It also adds a notion of global state to automata.
-Moreover, in \cite{henrio:Forte2016} the study of compositionality was only partial, and in particular the proof that bisimularity is an equivalence is one new contribution of this article and provides a particularly interesting insight on the semantic model we use.
+Moreover, in \cite{henrio:Forte2016} the study of compositionality was only partial, and in particular the proof that bisimilarity is an equivalence is one new contribution of this article and provides a particularly interesting insight on the semantic model we use.
 The new formalism allowed us to extend the work and define weak bisimulation  for open automata, which is entirely new.
@@
 cases where the original transition can be triggered. %\TODO{Eric: is this like in symbolic bisimulation ?}
-This is similar to the early and late symbolic bisimulation equivalences for value-passing CCS \cite{HENNESSY:1995}, though we use more general definitions in our setting.
+This is similar to the early and late symbolic bisimulation equivalences for value-passing CCS \cite{HennessyLin:TCS95}, though we use more general definitions in our setting.
 
@@
 the semantics of open pNets expressed as open automata, and states
-compositionality properties of strong bisimularity for open
+compositionality properties of strong bisimilarity for open
 pNets. 
@@
 The disjoint union on sets is $\uplus$ and we only use $A\uplus B$ when $A$ and $B$ are disjoint.
-We extend it to   union  of indexed sets provided they are indexed over disjoint families; is $\uplus$  is then defined by the merge of the
+We extend it to   union  of indexed sets provided they are indexed over disjoint families;  $\uplus$  is then defined by the merge of the
 two sets.
@@
 %methods of different interfaces).
-The  subtraction operation on indexed sets is $\setminus$, it reduces the set of indexes such that $\dom(A\setminus B)=\dom(A)\setminus B$.
+The  subtraction operation on indexed sets is $\setminus$, it reduces the set of indices such that $\dom(A\setminus B)=\dom(A)\setminus B$.
 
@@
 Each hole is represented by an empty disc, when the hole is filled it becomes a black disc.
-The left hole is
-  indexed $L$ the right hole $R$. The sub-net is an labelled transition system (LTS) with three states and emitting actions $l$ and $r$.
+The left hole is indexed by $L$ and the right hole by $R$. The sub-net is a LTS with three states and emitting actions $l$ and $r$.
 
@@
 Note that we make no assumption on finiteness of the set of states nor
-on finite branching of the transition relation. Compared to our previous works~\cite{henrio:Forte2016,AmeurBoulifa2017} make variables global, which makes the model easier to use.
+on finite branching of the transition relation. Compared to our previous works~\cite{henrio:Forte2016,AmeurBoulifa2017} we only global variables, which makes the model easier to use.
 
@@
 It is defined inductively (we suppose that those index sets are
-disjoints):
+disjoint):
   \[\begin{array}{l}
@@
 For example, the controller of Example~\ref{ex:CCSplus} has the sort $\{l,r\}$ and holes $\{L,R\}$.
-Note that  $\Holes(\pNet)$is a set of indexes because holes are characterized only by their indices, while entities at the leaves ar pLTSs and thus $\Leaves(\pNet)$ is a set of pLTSs.
+Note that  $\Holes(\pNet)$ is a set of indices because holes are characterized only by their indices, while entities at the leaves are pLTSs and thus $\Leaves(\pNet)$ is a set of pLTSs.
 A pNet $Q$ is \emph{closed} if it has no hole: $\Holes(Q)=\emptyset$; else it
@@
 We also adopt a semantics and logical interpretation of the automata that intuitively can be stated as follows: ``if a transition belongs to an open automaton, any refinement of this transition also belongs to the automaton''.
-{Our open automata are clearly inspired by the work  of De Simone on formatting of SOS rules~\cite{deSimone85}.
+{Our open automata are clearly inspired by the work  of De Simone on  SOS rule~\cite{deSimone85} formats.
 A precise comparison with related works can be found in Section~\ref{sec:RW}.}
@@
 
-While the definition and usage of the open transition can be considered purely syntactically, we take in this article a semantics and logical understanding of open automata. 
+While the definition and usage of the open transition can be considered purely syntactically, we take in this article a semantic and logical understanding of open automata. 
 We  see open transitions as logical formulas with a constrained syntax and logics rather than purely syntactical terms.
@@
  that pioneered this idea.
-Indeed, our definition uses both hypotheses on the behaviour of holes, as in \cite{deSimone85}, and symbolic manipulation of action expressions, as in symbolic bisimulations of \cite{HENNESSY:1995}. 
+Indeed, our definition uses both hypotheses on the behaviour of holes, as in \cite{deSimone85}, and symbolic manipulation of action expressions, as in symbolic bisimulations of \cite{HennessyLin:TCS95}.
 %\TODO{Eric: combination of RdS, symb bisim, and more}
@@
 The parametric nature of the automata entails a second original aspect of FH-bisimulation: the nature of the bisimulation relation itself.
- A classical relation between states can be seen as a function mapping pairs of state to a boolean value (true if the states are related, false if they are not).
+ A classical relation between states can be seen as a function mapping pairs of states to a boolean value (true if the states are related, false if they are not).
 An FH-bisimulation relation maps pairs of states to boolean expressions that use variables of the two systems.
@@
 
-\begin{thm}[FH-bisimularity is an equivalence]\label{thm-equiv} FH-bisimilarity is 
+\begin{thm}[FH-bisimilarity is an equivalence]\label{thm-equiv} FH-bisimilarity is 
 reflexive, symmetric and transitive.
@@
 
-	\begin{figure}[tb]\label{fig:Tr1Tr2}
+	\begin{figure}[tb]
 \[\inferrule
@@
 \caption{Rules \TrUn\ and \TrDeux\ defining the semantics of  open pNets}
+\label{fig:Tr1Tr2}
 \end{figure}
@@
 	\label{def:operationalSemantics} The semantics of a pNet $\pNet$ is an open automaton $A\!= 
-	\mylangle \symb{Holes}(\pNet),\symb{States}(\pNet),\symb{InitState}(\pNet),\symb{vars}(P),\mathcal{T} \myrangle$ where $\mathcal{T}$   is the smallest set of open transitions such that $\mathcal{T}=\{OT\,|\,\pNet \models OT \}$ and	$\pNet \models OT$	is defined by the rules in Figure~\ref{fig:Tr1Tr2}
+	\mylangle \symb{Holes}(\pNet),\symb{States}(\pNet),\symb{InitState}(\pNet),\symb{vars}(P),\mathcal{T} \myrangle$ where $\mathcal{T}$   is the smallest set of open transitions such that $\mathcal{T}=\{OT\,|\,\pNet \models OT \}$ and	$\pNet \models OT$	is defined by the rules in Figure~\ref{fig:Tr1Tr2}.
 %	\begin{itemize}
@@
 	\Holes(\pNet)$, $I_2=M\cap \Leaves(\pNet)$,  $I_1=M\setminus J \setminus 
-	I_2$}\footnote{We could replace $I_1$ and $I_2$ by their formal definition in \TrDeux\ but the rule would be more difficult to read.}.   
+	I_2$. We could replace $I_1$ and $I_2$ by their formal definition in \TrDeux\ but the rule would be more difficult to read.}.   
 \end{itemize}                                                                  
@@
 predicates.
-\begin{lem}[Open transition decomposition\label{lem-decompose}] Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$}.
+\begin{lem}[Open transition decomposition\label{lem-decompose}] Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$.}.
 	Let $\Leaves(Q)=p_l^{l\in L_Q}$ and suppose:
@@
 
-Then the effect of one single $100 \xrightarrow{OT_4} 210 \xrightarrow{OT_5} 220 \xrightarrow{OT_6} 100$ loop is\footnote{when showing  the result of $Posts$ composition, we will omit the identity substitution functions introduced by the $\shortodot$ definition in page \pageref{def:substitutions}}:
+Then the effect of one single $100 \xrightarrow{OT_4} 210 \xrightarrow{OT_5} 220 \xrightarrow{OT_6} 100$ loop is\footnote{when showing  the result of $Posts$ composition, we will omit the identity substitution functions introduced by the $\shortodot$ definition in page \pageref{def:substitutions}.}:
 \[post_{456} = post_6 \shortodot\ post_5 \shortodot\ post_4
@@
 The pNet does not satisfy Definition~\ref{def:non-obspNet}. Indeed, if $a$ or $b$ is $\tau$ then the $+$ operator can  observe the $\tau$ transition.
-It is well-known that weak bisimularity is not a congruence in CCS, this corresponds to the fact that the $+$ operator can observe the $\tau$ transitions.
+It is well-known that weak bisimilarity is not a congruence in CCS, this corresponds to the fact that the $+$ operator can observe the $\tau$ transitions.
 Thus, even if we can define a weak FH-bisimilarity for CCS with $+$ it does not verify the necessary requirements for being a congruence.
@@
 
-  Checking that $\mathcal{R}$ is a weak FH-bisimulation means checking, for each of these triples, that each (strong) OT of one the states corresponds to a set of WOTs of the other, using the conditions from Definition \ref{def-Weak-bisim}.
+  Checking that $\mathcal{R}$ is a weak FH-bisimulation means checking, for each of these triples, that each (strong) OT of one  of the states corresponds to a set of WOTs of the other, using the conditions from Definition \ref{def-Weak-bisim}.
   We give here one  example: consider the second triple from the table, and transition $SS_3$ from state \texttt{b0}.
@@
 \cite{Johnson:2013:CBSE,Johnson:2014:qosa}, the authors investigate several methodologies for the compositional verification of software systems, with the aim to verify reconfigurable component systems.
-To improve scaling and compositionality, the authors  decompose the verification problem that is to be resolved by a SMT (satisfiability modulo theory) solver into independent sub-problems on independent sets of variables.
+To improve scalability and compositionality, the authors  decompose the verification problem that is to be resolved by a SMT (satisfiability modulo theory) solver into independent sub-problems on independent sets of variables.
 These works clearly highlight the interest of incremental and compositional verification in a very general setting.
@@
 However, pNets feature hierarchical composition with more structure than mCRL2 that composes processes with a parallel operator.
-Synchronisation of processes is expressed very differently; it is difficult to precisely compare multi-actions of mCRL2 with synchronisation vectors of pNets but synchronisation vector ogf pNets enforce a  synchronisation based on the structure while in mCRL2 synchronisation is specified in a versatile, flexible, but less structured way.
+Synchronisation of processes is expressed very differently; it is difficult to precisely compare multi-actions of mCRL2 with synchronisation vectors of pNets but synchronisation vector of pNets enforce a  synchronisation based on the structure while in mCRL2 synchronisation is specified in a versatile, flexible, but less structured way.
 
@@
 \section{Proof on FH-bisimulation}
-\subsection{Bisimulation is an equivalence: Proof of Theorem~\ref{thm-equiv}}\label{thm-equiv-proof}~\\
+\subsection{Bisimilarity is an equivalence: Proof of Theorem~\ref{thm-equiv}}\label{thm-equiv-proof}~\\
         \emph{Suppose $\mathcal{R}$ 
-       	is an FH-bisimulation. Then $\mathcal{R}$ is an equivalence, that is, 
+       	is an FH-bisimilarity. Then $\mathcal{R}$ is an equivalence, that is, 
        	$\mathcal{R}$ is 
@@
        	states of 
-       		$\mathcal{T}_1,\,\mathcal{T}_2,\,\mathcal{T}_3$ for the sake of readability}.
+       		$\mathcal{T}_1,\,\mathcal{T}_2,\,\mathcal{T}_3$ for the sake of readability.}.
        	Suppose we have $\mathcal{R}$ an FH-bisimulation relation between states of 
@@
 \subsubsection*{{\bf Lemma~\ref{lem-decompose}}: Open transition decomposition} ~\\
- Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$}.
+ Consider two pNets $P$ and $Q$ that are not pLTSs\footnote{A similar lemma can be proven for a pLTS $Q$.}.
 	Let $\Leaves(Q)=p_l^{l\in L_Q}$; suppose:
@@
 We  define a quantified composition operator for effects, i.e. $\Post$ elements of the open transitions.
-We use ${\displaystyle \bigodot_{i=n}^{1} \Post_i}$ to denote  $\Post_n\otimes .. \otimes \Post_0$. By convention ${\displaystyle \bigodot_{i=0}^{1} \Post_i}$ is the identity.
+We use ${\displaystyle \bigodot_{i=n}^{1} \Post_i}$ to denote  $\Post_n\odot \ldots \odot \Post_0$. By convention ${\displaystyle \bigodot_{i=0}^{1} \Post_i}$ is the identity.
 
@@
 	lemma imply that $Q$ is 
-	not a pLTS but a similar lemma can be proven for a pLTS $Q$}:
+	not a pLTS but a similar lemma can be proven for a pLTS $Q$.}:
 	\[ P[Q]_{j_0}  
@@
 
-And thus, because $\beta_{pj}^{j\in J\cap \Holes(Q)}$ are equal to the concatenation of  $(\beta'_{1pj})^{j\in J\cap \Holes(Q)}$, $(\beta'_{2j})^{j\in J\cap \Holes(Q)}$, and $(\beta_{3pj}')^{j\in J\cap \Holes(Q)}$ (re-indexed because we skipped some transitions), and additionally $(\beta_{1pj}')^{j\in J\cap \Holes(Q)}$, $(\beta_{2j}')^{j\in J\cap \Holes(Q)}$, and $(\beta_{3pj}')^{j\in J\cap \Holes(Q)}$ are identical to the hole labels $\beta_{1kj}^{j\in J\cap \Holes(Q)}$, $\beta_{2j}^{j\in J\cap \Holes(Q)}$, and $\beta_{3kj}^{j\in J\cap \Holes(Q)}$ (re-indexed) when $Q$ moves\footnote{more precisely, when $Q$ moves either $\beta_{1kj}^{j\in J\cap \Holes(Q)}$ is not empty  and thus $(\beta_{1pj}')^{j\in J\cap \Holes(Q)}=\beta_{1kj}^{j\in J\cap \Holes(Q)}$, or both are empty if the holes of $Q$ perform no action}.
+And thus, because $\beta_{pj}^{j\in J\cap \Holes(Q)}$ are equal to the concatenation of  $(\beta'_{1pj})^{j\in J\cap \Holes(Q)}$, $(\beta'_{2j})^{j\in J\cap \Holes(Q)}$, and $(\beta_{3pj}')^{j\in J\cap \Holes(Q)}$ (re-indexed because we skipped some transitions), and additionally $(\beta_{1pj}')^{j\in J\cap \Holes(Q)}$, $(\beta_{2j}')^{j\in J\cap \Holes(Q)}$, and $(\beta_{3pj}')^{j\in J\cap \Holes(Q)}$ are identical to the hole labels $\beta_{1kj}^{j\in J\cap \Holes(Q)}$, $\beta_{2j}^{j\in J\cap \Holes(Q)}$, and $\beta_{3kj}^{j\in J\cap \Holes(Q)}$ (re-indexed) when $Q$ moves\footnote{more precisely, when $Q$ moves either $\beta_{1kj}^{j\in J\cap \Holes(Q)}$ is not empty  and thus $(\beta_{1pj}')^{j\in J\cap \Holes(Q)}=\beta_{1kj}^{j\in J\cap \Holes(Q)}$, or both are empty if the holes of $Q$ perform no action.}.
 We can assert a similar equality on post-conditions, i.e.
@@
 Note also that $\Post$ only acts on variables of $P$ while $\Post_{1i}$ only acts on  variables of $Q$.
-We conclude on predicate and posts as follows\footnote{$\Post_{1i}$ only has an effect on variables of $Q$ and thus does not modify $\Pred$ or $\beta_{j_0}$}:
+We conclude on predicate and posts as follows\footnote{$\Post_{1i}$ only has an effect on variables of $Q$ and thus does not modify $\Pred$ or $\beta_{j_0}$.}:
 \begin{equation*}
@@
 state b1
-transition out(b_msg, b_ec) -> a0
+transition out(b_msg, b_ec) -> b0
 transition synchro(tau())  -> b1 {b_ec:=b_ec+1}
@@
 
-         Note that if we were using the alternative weak FH-bisimulation relation from Appendix \ref{app-WFH-equiv}, Lemma \ref{lem-rel-OT-WOT}, that is checking strong FH-bisimulation between the corresponding
+         Note that if we were using the alternative weak FH-bisimulation relation from \ref{app-WFH-equiv}, Lemma \ref{lem-rel-OT-WOT}, that is checking strong FH-bisimulation between the corresponding
 weak automaton, we would have a more transitions coverage to examine, as we have 4 weak transitions for $b0$ in the \symb{SimpleProtocolSpec} weak automaton, and 7 WOTs (including 4 
@@
       condition: the only vectors having $\tau$ as an action of a
-      sub-net are of the form ``$< -, \tau, -> -> \tau$''.
+      sub-net are of the form ``$< -, \tau, -> \rightarrow \tau$''.
     \item We must take care of variable name conflicts: in our example, the variables of the 2 systems already have different names, but the action parameters occurring in the 

### 2022-11-23 2016-Weak-FH-Bisim/WeakBisim.tex
Other corrections

@@
 
-We let $e_i$ range over expressions ($e_i\in\AlgE$), $a$
-range over action labels, $\symb{op}$ be operators, and $x_i$ and $y_i$ range over
-variable names. We additionally rely on a set of action names, ranged over by $a$, $b$, \ldots
-
+We let $e_i$ range over expressions ($e_i\in\AlgE$), $\symb{op}$ be operators, and $x_i$ and $y_i$ range over
+variable names.  We additionally rely on a set of action names, ranged over by $a$, $b$, \ldots. 
 We define two kinds of parameterised actions.
@@
 The second kind makes no distinction between input and output parameters.
-The  actions that distinguish input variables will be used in the definition of \pLTS\ below and are defined as follows:
+The  actions that distinguish input variables will be used in the definition of \pLTS\  and are defined as follows:
 \[
@@
 
+Note that, if there is a FH-bisimulation $\mathcal{R}$ such  that $(s,t|\Pred)\in\mathcal{R}$, and additionally $\Pred\,'\Rightarrow \Pred$ and  it does not mean that there is a FH-bisimulation $\mathcal{R}'$ such that $(s,t|\Pred\,')$, indeed pair of states such that $\Pred$ is true and $\Pred\,'$ is false might be necessary to prove the FH-bisimulation.
 \begin{example}
@@
  $ \forall n\ge 1.  WI_{8b}(n) = \openrule
-         {\{\texttt{Q}\mapsto \texttt{q-recv(??\_msg,s\_ec}+n)\}, True, ()}
-         {220 \OTWeakarrow {\nounderline{\texttt{out(??\_msg,m\_ec}+n)}} \{202, 000\}}
+         {\{\texttt{Q}\mapsto \texttt{q-recv(s\_msg,s\_ec}+n)\}, True, ()}
+         {220 \OTWeakarrow {\nounderline{\texttt{out(s\_msg,m\_ec}+n)}} \{202, 000\}}
          $

### 2022-11-30 2021-Refinement/paper/refinementarticleV2.tex
version 2 du papier avec def revisee

--- 2022-07-17 2021-Refinement/paper/refinementarticle.tex
@@
 Finally, we should take into account that 1) instead of equality, we should check if there is a state such that both transitions are feasible (the conjunction of guards is satisfiable), and that  2) instead of finding another transition of the specification we might find a family of transitions that cover all the cases of the transition of the implementation.
-This leads us to the following definition.
-\begin{definition}[Preservation along identical transitions]\label{def:preservation} \\
-Let \(\OAg[1]\) and \(\OAg[2]\) be two OAs.
-A relation \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) between  \(\OAg[1]\) and \(\OAg[2]\)
-  is preserved along identical transitions if  it satisfies the following:
-% TODO: isn't it a2 = a1x instead of a1x = a1
-% TODO: ANS:  we have a1 = a2 so whatever, it is the same, we can change if it is more ``natural''
-\begin{multline*}
-\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_2} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\ 
-\bigsymb{\bigexists} 
-\mpar{t_{1x} \!=\! \OTx{1}{x}{1x}{1x} \!\in\! \fOT{s_1}}^{x \in X}\!,
- V_1 \uplus V_2 \uplus \biguplus_{x\in X}\!\fvars{t_{1x}} \uplus \fvars{t_2} \uplus \fvars{t_1} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 
-%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} 
-\implies \\
-%\exists
-%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
-\bigsymb{\bigwedge_{x\in X}}
-\mpar{
-\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_2 \land \bigwedge_\subbox{j \in J'_2 } \beta_{2j} = \beta_{1xj}\land g_{1 x}\land
- R\mpar{s'_{1 x}, s'_2}\psubst{\psi_{1 x} \uplus \psi_2}}\\
-\end{multline*}
-\end{definition}
 
@@
 This relation thus focuses on the simulation of transitions and uses the previous definition to prevent the refined automaton from non-deterministically reaching states that introduce deadlocks in a scenario planned without deadlock in the specification.
+\TODO{Changement de la definition de simulation pour selon la simulation de Olga}
+
 \begin{definition}[Hole-equal simulation]
@@
 \noindent\begin{multline*}
+\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_2} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\ 
 \everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} t_1 = \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\[10pt]
-		\quad \mpar{\forall x \in X, J'_{2x}= J'_1} \nwedge\\[2pt]
-		 V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\
-\hspace{5em} \left( R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x}} \beta_{1j} = \beta_{2xj} \nwedge\\[12pt]
-			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}}\right)
+V_1 \uplus V_2 \uplus \fvars{t_1} \uplus \fvars{t_2}  \vdash R\mpar{s_1, s_2} \wedge g_2 \implies\\
+V_1 \uplus V_2 \uplus \fvars{t_{1x}} \uplus \fvars{t_2}\vdash  \bigsymb{\bigexists} 
+\mpar{t_{1x} \!=\! \OTx{1}{x}{1x}{1x}}^{x \in X} \operatorname*{\bigsymb{\bigvee}}_{x \in X}
+\mpar{\begin{array}{l}
+			\alpha_{1x} = \alpha_{2} \wedge \bigwedge_\subbox{j \in J'_{2}} \beta_{1xj} = \beta_{2j} \nwedge\\[12pt]
+			 g_{1x} \wedge R\mpar{s'_{1x}, s'_{2}}\psubst{\psi_{1x} \uplus \psi_{2}}
+		\end{array}} 
 \end{array} 
-%\\
-%	\wedge \mpar{V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
 \end{multline*}
-\item[(3)] $R$ is  is preserved along identical transitions of \(A_1\) and \(A_2\).
+\item [(3)] The deadlock reduction:
+\begin{multline*}
+\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge  \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}
+\end{multline*}
+
 \end{definition}
+
+\TODO{To discuss this definition}
 
@@
 \section{Proof of Transitivity for Refinement}\label{sec:proof-transitivity}
-\begin{quote}
-If $\wrel{A_1}{A_2}{H}$ and $\wrel{A_2}{A_3}{H'}$, then $\wrel{A_1}{A_3}{H\cap H'}$.
-\end{quote}
-\proof 
-If $\wrel{A_1}{A_2}{H}$ then there is $R_{12}$ a relation between states
-of $A_1$ and of $A_2$;  If $\wrel{A_2}{A_3}{H'}$ then there is $R_{23}$ a relation between states of $A_2$ and of $A_3$. We build a relation between
- states of $A_1$ and of $A_3$ as follows:  for each pair of states $s_1$, $s_3$, for each state $s_2$ such that $R_{12}$ relates $s_1$ and $s_2$, and $R_{23}$ relates $s_2$ and $s_3$.
-Let $R_{13}$ be the relation:\\
-  \[R_{13}(s_1,s_3)=\bigvee_{s_2\in S_2}\mpar{R_{12}(s_1,s_2) \land R_{23}(s_2,s_3) } \]
-
-We will show that $\wrel{A_1}{A_3}{H\cap H'}$ by exhibiting  $R_{13}$ as a hole-tracking simulation of $A_1$ by  $A_3$.
-
-We have to prove that the relation $R_{13}$ satisfies the three conditions of the definition of a refinement of open automata.
-\begin{enumerate}
-\item Firstly, we have to $R_{13}$ satisfies initial configurations:
-\[\sigma_{01} \uplus \sigma_{03} \vdash R_{13} \mpar{s_{01}, s_{03}}\]
-By knowing that substitutions only have an effect on the variables of the open automaton they belong to, they also produce terms containing only variables of the open automaton they belong to.
-We have:
-\begin{align*}
-\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar
-{\sigma_{02} \uplus \sigma_{03} \vdash R_{23}\mpar{s_{02}, s_{03}}}&\implies\\
-R_{12}\mpar{s_{01},s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02}} \wedge R_{23}\mpar{s_{02}, s_{03}}\psubst{\sigma_{02} \uplus \sigma_{03}}&\implies\\
-R_{12}\mpar{s_{01},s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} \wedge R_{23}\mpar{s_{02}, s_{03}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}}&\implies\\ 
-\underbrace{R_{12}\mpar{s_{01},s_{02}}\wedge R_{23}\mpar{s_{02}, s_{03}}}_{\implies R_{13} \mpar{s_{01}, s_{03}}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} %&\implies\\
- \end{align*}
-Since $\sigma_{02}$ has no effect on variables of $s_{01}$ and $s_{03}$ thus we get the expected result.
-
-\item Secondly, we need to prove that for any open transition $t_1$ in $T_1$  originating from $s_1$:
-\begin{align*}
-\OTx{1}{}{1}{1} \in \fOT{s_1}
-\end{align*}
-there exists an indexed family of OTs originating from $s_{3}$: 
-\begin{multline*}
-V_1 \uplus  V_3 \uplus \fvars{t_1}
-\vdash\\\hspace{2em}
-\mpar{R_{13}\mpar{s_1, s_3} \wedge g_1 \implies 
-\operatorname*{\bigsymb{\bigvee}}_{z \in Z}
-\mpar{\everymath{\displaystyle}
-\begin{array}{l}
-\alpha_1=\alpha_{3z}\wedge \bigwedge_\subbox{j \in J'_{3z} \cap (H\cap H')} \beta_{1j}=\beta_{3jz} \wedge \\g_{3z}\wedge 
-{R_{12}\mpar{s'_1,s'_{3z}}}\psubst{\psi_1  \uplus \psi_{3z}}
-\end{array}}}
-\end{multline*}	
-\medskip
- Consider $\mpar{s_{1}, s_{3}} \in R_{13}$ then there is a set of states $(s_{2p})^{p\in P}$ of $A_2$ relating  $s_{1}$ and $s_{3}$:
-\[R_{13}(s_1,s_3)=\bigvee_{{p\in P}
-}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}} \]
-
-Let's consider any $s_{2p} \in (s_{2p})^{p\in P}$. We have on one side,  for any open transition $t_1$ in $T_1$  originating from $s_1$:
-\begin{align*}
-\OTx{1}{}{1}{1} \in \fOT{s_1}
-\end{align*}
-there exists an indexed family of OTs originating from $s_{2p}$: 
-\begin{align*}
-\mpar{\OTx{2p}{x}{2px}{2px} \in \fOT{s_{2p}}}^{x \in X_p} 
-\end{align*}
-such that $\forall x \in X, J'_{2px} \cap H = J'_1 \cap H$ and
-\begin{multline*}
-%\everymath{\displaystyle}
-V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\ \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X_p} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \nwedge\\
-			 g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}}
-		\end{array}}} 
-\end{multline*}		
-Adding to both sides of the implication the predicate $R_{23}\mpar{s_{2p},s_3}$ we get: 
-\begin{multline*}
-V_1 \uplus V_2 \uplus V_3  \uplus \fvars{t_1} \vdash\\
-R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies\hspace{5.5cm}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \land\\
-			 g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}} \land R_{23}\mpar{s_{2p},s_3}
-		\end{array}} \qquad (*) 
-\end{multline*}	
-On the other side, according the relation between $A_2$ and $A_3$ we have for any open transition $t_{2px}$ in $T_2$ originating from $s_{2p}$:
-\begin{align*}
-\OTx{2p}{x}{2px}{2px} \in \fOT{s_{2p}}
-\end{align*}
-there exists an indexed family of OTs originating from $s_3$: 
-\begin{align*}
-\mpar{\OTx{3}{pxy}{3pxy}{3pxy} \in \fOT{s_3}}^{y \in Y} 
-\end{align*}
-such that $\forall y \in Y, J'_{2px} \cap H' = J'_{3pxy} \cap H'$ and
-\begin{multline*}
-%\everymath{\displaystyle}
-V_2 \uplus V_3 \uplus \fvars{t_{2px}} \vdash\\
-R_{23}\mpar{s_{2p}, s_{3}} \wedge g_{2px} \implies \hspace{7cm}\\ \operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			 \alpha_{2px}=\alpha_{3pxy} \wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{2pxj}=\beta_{3pxyj} \nwedge \\
-			g_{3pxy} \wedge R_{23}\mpar{s'_{2px}, s'_{3xy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
-		\end{array}}  \qquad (**)
-\end{multline*}
-
-From the  two previous cases: 
-$\forall x \in X, J'_{2px} \cap H = J'_1 \cap H$ and
-$\forall y \in Y, J'_{2px} \cap H' = J'_{3pxy} \cap H'$ we conclude:
-$\forall x \in X, \forall y \in Y,  J'_1 \cap (H \cap H') = J'_{3pxy} \cap (H\cap H')$ \\
-
-In addition, by combining  formula $(**)$ and $(*)$, we get: 
-\begin{multline*}
-V_1 \uplus V_2 \uplus V_3  \uplus \fvars{t_1}\uplus \fvars{t_{2px}} \vdash\\
-R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies \hspace{4.5cm}\\\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj}  \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}} \\ 
-\land
-		\operatorname*{\bigsymb{\bigvee}}_{y \in Y} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			 \alpha_{2px}=\alpha_{3pxy} \wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap H'} \beta_{2pxj}=\beta_{3pxyj} \nwedge\\
-			 g_{3pxy} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
-		\end{array}}	
-		\end{array}} 
-\end{multline*}		
-With  the rearrangement of the formula, we get:
-\begin{multline*}
-V_1 \uplus V_2 \uplus V_3  \uplus \fvars{t_1}\uplus \fvars{t_{2px}}  \vdash\\
-R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies 
-\hspace{5.5cm}\\
-\operatorname*{\bigsymb{\bigvee}}_{x \in X} 
-\operatorname*{\bigsymb{\bigvee}}_{y \in Y}
-\mpar{\everymath{\displaystyle}
-\begin{array}{l}
-\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap (H\cap H')} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
-R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_{2px} \uplus \psi_{3pxy}}
-\end{array}}
-\end{multline*}
-
-Because of the domain of the substitutions of the relations, the formula can be re-written:
-\begin{multline*}
-V_1 \uplus V_2 \uplus V_3  \uplus \fvars{t_1}\uplus \fvars{t_{2px}} \vdash\\
-R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1 \implies 
-\hspace{5.5cm}\\
-\operatorname*{\bigsymb{\bigvee}}_{x \in X} 
-\operatorname*{\bigsymb{\bigvee}}_{y \in Y}
-\mpar{\everymath{\displaystyle}
-\begin{array}{l}
-\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap (H\cap H')} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
-\mpar{R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}
-\end{array}}
-\end{multline*}
-The formula is valid for all $s_{2p} \in (s_{2p})^{p\in P}$.
-To build $R_{13}$ we need to rely on the disjunction of all possible paths to relate $s_1$ and $s_3$, which leads to\\ ${\displaystyle R_{13}(s_1,s_3)=\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}}$.
-\begin{multline*}
-V_1 \uplus V_2 \uplus V_3  \uplus \fvars{t_1} \uplus  \biguplus_\subbox{p \in P} \fvars{t_{2px}} \vdash\\
-\operatorname*{\bigsymb{\bigvee}}_{p\in P} \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \wedge g_1} \implies 
-\hspace{5.5cm}\\
-\operatorname*{\bigsymb{\bigvee}}_{p\in P}
-\operatorname*{\bigsymb{\bigvee}}_{x \in X} 
-\operatorname*{\bigsymb{\bigvee}}_{y \in Y}
-\mpar{\everymath{\displaystyle}
-\begin{array}{l}
-\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap (H\cap H')} \beta_{1j}=\beta_{3jpxy} \wedge g_{3pxy}\wedge \\
-\underbrace{R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}}_{\implies R_{13}\mpar{s'_1,s'_{3pxy}}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}
-\end{array}}
-\end{multline*}
-Indeed, since $\psi_{2px}$ has no effect on variables of $A_1$ and $A_3$ we have:
-\begin{align*}
-R_{12}\mpar{s'_1, s'_{2px}} \wedge R_{23}\mpar{s'_{2px}, s'_{3pxy}}\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}  \\  
-\implies R_{13}\mpar{s'_1,s'_{3pxy}}
-\psubst{\psi_1 \uplus \psi_{2px} \uplus \psi_{3pxy}}  \\ 
-\implies R_{13}\mpar{s'_1,s'_{3pxy}}\psubst{\psi_1  \uplus \psi_{3pxy}}
-\end{align*}
-This allows us to conclude that the family of open transitions of $A_3$ indexed over $p$, $x$,  and $y$ simulates the original open transition  with note that $\psi_{2px}$ has no effect on variables of $A_1$ and $A_3$:
-\begin{multline*}
-V_1  \uplus V_3  \uplus \fvars{t_1} \vdash\\
-R_{13}(s_1,s_3)  \wedge g_1 \implies 
-\hspace{5.5cm}\\
-\operatorname*{\bigsymb{\bigvee}}_{p\in P}
-\operatorname*{\bigsymb{\bigvee}}_{x \in X} 
-\operatorname*{\bigsymb{\bigvee}}_{y \in Y}
-\mpar{\everymath{\displaystyle}
-\begin{array}{l}
-\alpha_1=\alpha_{3pxy}\wedge \bigwedge_\subbox{j \in J'_{3pxy} \cap (H\cap H')} \beta_{1j}=\beta_{3jpxy} \\ \wedge g_{3pxy} 
-{\wedge R_{13}\mpar{s'_1,s'_{3pxy}}}\psubst{\psi_1  \uplus \psi_{3pxy}}
-\end{array}}
-\end{multline*}
-Overall, we have a family of open transitions $t^{p\in P,x\in X,y\in Y}_{pxy} \subseteq T_3$ that should simulate $t_1$.
-All  combinations of elements in $P$, $X$, and $Y$ provide a set $Z$ of  open transitions.
-This allows us to get the desired conclusion, that there is a set of  open transitions indexed over $Z$:
-%This provides the desired conclusion:\\
-\begin{multline*}
-V_1 \uplus  V_3 \uplus \fvars{t_1}
-\vdash\\\hspace{2em}
-\mpar{R_{13}\mpar{s_1, s_3} \wedge g_1 \implies 
-\operatorname*{\bigsymb{\bigvee}}_{z \in Z}
-\mpar{\everymath{\displaystyle}
-\begin{array}{l}
-\alpha_1=\alpha_{3z}\wedge \bigwedge_\subbox{j \in J'_{3z} \cap (H\cap H')} \beta_{1j}=\beta_{3jz} \wedge \\g_{3z}\wedge 
-{R_{13}\mpar{s'_1,s'_{3z}}}\psubst{\psi_1  \uplus \psi_{3z}}
-\end{array}}}
-\end{multline*}
-
-\item  Finally, we have to prove the following holds:
-\begin{multline*}
-\bigforall \mpar{s_1, s_3} \in S_1 \times S_3, \bigsymb{\forall} \mpar{t_1, t_3} = \mpar{\OTx{1}{}{1}{1}, \OTx{3}{}{3}{3}} \in \fOT{s_1} \times \fOT{s_3} \\ 
-\bigsymb{\bigexists} 
-\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},
- V_1 \uplus V_3\uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_3} \vdash \hspace{6cm}\\  R_{13}\mpar{s_1, s_3} \wedge 	g_1 \wedge g_3 \wedge \alpha_1 = \alpha_3 
-%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_3} \beta_{1j} = \beta_{3j} 
-\implies \hspace{6cm}\\
-%\exists
-%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
-\bigsymb{\bigwedge_{x\in X}}
-\mpar{
-\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{1xj}\land g_{1 x}\land
- R_{13}\mpar{s'_{1 x}, s'_3}\psubst{\psi_{1 x} \uplus \psi_3}}
-\end{multline*}
-
- Consider $\mpar{s_{1}, s_{3}} \in R_{13}$ then there is a set of states $(s_{2p})^{p\in P}$ of $A_2$ relating  $s_{1}$ and $s_{3}$:
-\[R_{13}(s_1,s_3)=\bigvee_{{p\in P}
-}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}} \]
-
-\newpage
-\TODO{[RABEA] proof}
-Let's consider any $s_{2p} \in (s_{2p})^{p\in P}$. According to the refinement relation between  $A_1$ and $A_2$, we have  the following formula that we denote ($*$):\\
-for any open transition $t_1$ in $T_1$  originating from $s_1$:
-\begin{align*}
-\OTx{1}{}{1}{1} \in \fOT{s_1}
-\end{align*}
-there exists an indexed family of OTs originating from $s_{2p}$: 
-\begin{align*}
-\mpar{\OTx{2p}{x}{2px}{2px} \in \fOT{s_{2p}}}^{x \in X_p} 
-\end{align*}
-such that $\forall x \in X, J'_{2px} \cap H = J'_1 \cap H$ and
-\begin{multline*}
-%\everymath{\displaystyle}
-V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\ \mpar{R_{12}\mpar{s_1, s_{2p}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X_p} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_1 = \alpha_{2px} \wedge \bigwedge_\subbox{j \in J'_{2px} \cap H} \beta_{1j} = \beta_{2pxj} \nwedge\\
-			 g_{2px} \wedge R_{12}\mpar{s'_1, s'_{2px}}\psubst{\psi_1 \uplus \psi_{2px}}
-		\end{array}}} 
-\end{multline*}	
-On the other hand, according to the refinement relation between   $A_2$ and $A_3$, we know condition 3 is satisfied, $\bigforall \mpar{s_{2p}, s_3} \in S_1 \times S_3$ and $\bigsymb{\forall} \mpar{t_{2p}, t_3} \in \fOT{s_{2p}} \times \fOT{s_3}$ and in particular for  the set $(t_{2px})^{x\in X_p}$ so we  have the following that we denote ($**$):
-\begin{multline*}
-\bigsymb{\forall} \mpar{t_{2px}, t_3} = \mpar{\OTx{2px}{}{2px}{2px}, \OTx{3}{}{3}{3}} \in \fOT{s_{2p}} \times \fOT{s_3} \\ 
-\bigsymb{\bigexists} 
-\mpar{t_{2pxy} = \OTx{2px}{y}{2pxy}{2pxy} \in \fOT{s_{2p}}}^{y \in Y_X},
-V_2 \uplus V_3\uplus \biguplus_{y\in Y}\fvars{t_{2pxy}} \uplus \fvars{t_3} \uplus \fvars{t_{2p}} \vdash \hspace{6cm}\\  R_{23}\mpar{s_{2p}, s_3} \wedge 	g_{2px}\wedge g_3 \wedge \alpha_{2px}= \alpha_3
-%\wedge \bigwedge_\subbox{j \in J'_2 \cap J'_3} \beta_{2pj} = \beta_{3j} 
-\implies \hspace{6cm}\\
-%\exists
-%\OTx{1}{a}{3}{3}\in \fOT{s_2}. \\
-\bigsymb{\bigwedge_{y\in Y_X}}
-\mpar{
-\alpha_{2px}=\alpha_{2p xy}  \land J'_{2pxy}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{2pxyj}\land g_{2p xy}\land
- R_{23}\mpar{s'_{2p xy}, s'_3}\psubst{\psi_{2p xy} \uplus \psi_3}}\\
-\end{multline*}
-Again according to the refinement  relation between  $A_1$ and $A_2$ and condition 3  the following is satisfied $\bigforall \mpar{s_1, s_{2p}} \in S_1 \times S_2$ , in particular over the family of transitions in $(t_{2pxy})^{y\in Y_X}$:
-\begin{multline*}
-\bigsymb{\forall} \mpar{t_1, t_{2pxy}} = \mpar{\OTx{1}{}{1}{1}, \OTx{2pxy}{}{2pxy}{2pxy}} \in \fOT{s_1} \times \fOT{s_{2p}} \\ 
-\bigsymb{\bigexists} 
-\mpar{t_{1z} = \OTx{1}{z}{1z}{1z} \in \fOT{s_1}}^{z \in Z},
- V_1 \uplus V_2 \uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_{2p}} \vdash \hspace{6cm}\\  R_{12}\mpar{s_1, s_{2p}} \wedge 	g_1 \wedge g_{2pxy} \wedge \alpha_1 = \alpha_{2pxy}
-%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2p}} \beta_{1j} = \beta_{2pxyj} 
-\implies \hspace{6cm}\\
-%\exists
-%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
-\bigsymb{\bigwedge_{z\in Z}}
-\mpar{
-\alpha_1=\alpha_{1 z}  \land J'_{1z}= J'_{2pxy} \land \bigwedge_\subbox{j \in J'_{2pxy} } \beta_{2pxyj} = \beta_{1zj}\land g_{1 z}\land
- R_{12}\mpar{s'_{1 z}, s'_{2pxy}}\psubst{\psi_{1 z} \uplus \psi_{2pxy}}}
-\end{multline*}
-
-This is verified for all $y \in  Y_X$.
-\begin{multline*}
-\bigsymb{\bigwedge_{y \in  Y_X}}
-\Bigg[R_{12}\mpar{s_1, s_{2p}} \wedge 	g_1 \wedge g_{2pxy} \wedge \alpha_1 = \alpha_{2pxy}
-\implies \hspace{6cm}\\
-\bigsymb{\bigwedge_{z\in Z}}
-\mpar{
-\alpha_1=\alpha_{1 z}  \land J'_{1z}= J'_{2pxy} \land \bigwedge_\subbox{j \in J'_{2pxy} } \beta_{2pxyj} = \beta_{1zj}\land g_{1 z}\land
- R_{12}\mpar{s'_{1 z}, s'_{2pxy}}\psubst{\psi_{1 z} \uplus \psi_{2pxy}}}\Bigg]
-\end{multline*}
-
-The conjunction of formulas ($*$) and ($**$) gives:
-\begin{multline*}
-\bigsymb{\bigwedge_{y \in  Y_X}}
-\Bigg[
-\mpar{R_{12}\mpar{s_1, s_{2p}} \wedge 	g_1 \wedge g_{2pxy} \wedge \alpha_1 = \alpha_{2pxy}} \wedge \mpar{ R_{23}\mpar{s_{2p}, s_3} \wedge 	g_{2px}\wedge g_3 \wedge \alpha_{2px}= \alpha_3 } 
-\implies \hspace{6cm}\\
-%\exists
-%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
-\bigsymb{\bigwedge_{z\in Z}}
-\mpar{
-\alpha_1=\alpha_{1 z}  \land J'_{1z}= J'_{2pxy} \land \bigwedge_\subbox{j \in J'_{2pxy} } \beta_{2pxyj} = \beta_{1zj}\land g_{1 z}\land
- R_{12}\mpar{s'_{1 z}, s'_{2pxy}}\psubst{\psi_{1 z} \uplus \psi_{2pxy}}} \wedge \\
-\mpar{
-\alpha_{2px}=\alpha_{2p xy}  \land J'_{2pxy}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{2pxyj}\land g_{2p xy}\land
- R_{23}\mpar{s'_{2p xy}, s'_3}\psubst{\psi_{2p xy} \uplus \psi_3}}
- \Bigg]
-\end{multline*}
-By rearranging the formula we get:
-\begin{multline*}
-\bigsymb{\bigwedge_{y \in  Y_X}}
-\Bigg[
-R_{12}\mpar{s_1, s_{2p}} \wedge  R_{23}\mpar{s_{2p}, s_3} \wedge g_1 \wedge g_3 \wedge 	g_{2px}\wedge g_{2pxy} \wedge \alpha_1 = \alpha_{2pxy} \wedge     \alpha_{2px}= \alpha_3 
-\implies \hspace{6cm}\\
-%\exists
-%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
-\bigsymb{\bigwedge_{z\in Z}}
-\mpar{
-\alpha_1=\alpha_{1 z}  \land J'_{1z}= J'_{2pxy} \land \bigwedge_\subbox{j \in J'_{2pxy} } \beta_{2pxyj} = \beta_{1zj}\land g_{1 z}\land
- R_{12}\mpar{s'_{1 z}, s'_{2pxy}}\psubst{\psi_{1 z} \uplus \psi_{2pxy}}} \wedge \\
-\mpar{
-\alpha_{2px}=\alpha_{2p xy}  \land J'_{2pxy}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{2pxyj}\land g_{2p xy}\land
- R_{23}\mpar{s'_{2p xy}, s'_3}  \psubst{\psi_{2p xy} \uplus \psi_3}}
- \Bigg]
-\end{multline*}
-\TODO{ Je suis bloque a ce niveau: dans la conclusion on a $\alpha_{2px}=\alpha_{2p xy}$ qui est dans les hypotheses.  
-}
-
-The formula is valid for all  $s_{2p} \in (s_{2p})^{p\in P}$. To build $R_{13}$ we need to rely on the disjunction of all possible path to relate $s_1$ and $s_3$:
-
-Note that if  either $R_{12}\mpar{s_1, s_2}$ or $R_{23}\mpar{s_2, s_3}$ is false the statement trivially holds.
-So for each $s_2 \in S_2$, we remark that  $s_2$  allows to relate $s_1$ and $s_3$ if and only if $R_{12}\mpar{s_1, s_2}\land R_{23}\mpar{s_2, s_3} $.
-We pick a state $s_2$ relating both,  we can then the following be inferred from the above formulas:
-$\forall \mpar{s_1,s_3} \in S_1 \times S_3$ and\\ $\bigsymb{\forall} \mpar{t_1, t_{3}}\!=\! \mpar{\OTx{1}{}{1}{1},\OTx{3}{}{3}{3}}\! \in\! \fOT{s_1} \times \fOT{s_3}$
-
-By rearranging, simplifying and removing the variables of $A_2$ that have not effect on   $A_1$ et  $A_3$, we get the desired result.
-
-\end{enumerate}
-
-~\qed
-
-\section{Proof of Context Refinement (Theorem~\ref{thm:ContextRefinement})}
-
-\begin{quote}
-Suppose that $\wrel{A_1}{A_2}{H}$, \(k \in H\) and that \(A_1\subst{A_3}{k}\) is non-blocking.
-We have: \[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{J_3 \uplus H \setminus \mbrc{k}}\]
-\end{quote}
-
-\proof
-Let us denote by $A_{13}$ (resp.
-$A_{23}$) the open automaton resulting from $A_1\subst{A_3}{k}$ (resp.
-$A_2\subst{A_3}{k}$),  to prove the theorem it is sufficient to prove that there exists a relation between states of the two open automata that satisfies the conditions of the Definition \ref{Def:OA-Refinement}.
-
-We denote $A_1=  \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}$ and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and $A_3 = \OA{S_3}{s_{03}}{J_3}{V_3}{\sigma_{03}}{T_3}$.
-The proof requires  to rename the variables of one instance of the two $A_3$ automata to avoid clashes in variable names (this is required by the definition of refinement).
-In practice we will use superscripts ${}^1$ and ${}^2$ to distinguish elements of the two instances of $A_3$.
-
-Let $R$ be the refinement relation relating states of $A_1$ and $A_2$. 
-Let us denote with $t^1$ and $t^2$  the elements of $A_1$ and $A_2$ respectively.
-Consider any two states $s_{13} = \mpar{s_1,s^1_3}$ and $s_{23} = \mpar{s_2,s^2_3}$ ($s^1_3$ and $s^2_3$  are the same with renaming).
-We define a relation $R'$ relating states of $s_{13}$ and $s_{23}$ as follows:
-\[ R' \mpar{s_{13}, s_{23}} = R\mpar{s_{1}, s_{2}}  %\wedge \reach{A_{13}}\mpar{s_{13}}
- \wedge \bigwedge_\subbox{v_3\in V_3}
- v^1_3=v^2_3\wedge s^1_3 = s^2_3\]
-
-%\TODO{[Ludo] I believe reachability is not useful here -- to check}
-
-We want to prove that $\mpar{R', H\uplus J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$. In the following we denote $H'=H\cup J_3 \setminus\{k\}$.
-\begin{enumerate}
-\item First, we have to prove the relation for initial states:
-\[\sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}\]
-with $\sigma_{013} = \sigma_{01} \uplus \sigma_{03}^1$, $\sigma_{023} = \sigma_{02} \uplus \sigma_{03}^2$, $s_{013}=(s_{01},s_{03}^1)$, and $s_{023}=(s_{02},s_{02}^2)$.\\
-By using the fact that $R$ relates initial configurations of  $A_1$ and $A_2$, we have:
-$\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}}$.  
-%and based on the  fact that initial states are reachable $\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ we have 
-%\[ \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
-%\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\]
-
-Considering that initial valuations $\sigma_{03}^1$ and $\sigma_{03}^2$ associate the same values to the ``same'' variables modulo renaming, so the following holds:\\ $\left(\,\,{\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }$.
-
-Additionally, because  the domains of the substitution function are disjoint, the substitution function has an effect only on the related elements,  we get:
-\begin{align*}
-& \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} 
-%\wedge \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}
-\\
-\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}}  \land \mpar{\,\,\bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }\\
-\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge  \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma^1_{03}\uplus \sigma^2_{03}\uplus \sigma_{013} }\\
-\implies & \sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}
-\end{align*}
-\item Second, we need to prove for any open transition $t_{13}$ in $T_{13}$ originating from $s_{13}$:
-\begin{align*}
-		&  \OTx{13}{}{13}{13} \in \fOT{s_{13}}
-\end{align*}		
-there exists an indexed family $t_{23x}$ of OTs originating from $s_{23}$ that simulate it: 
-\begin{align*}
-		&  \mpar{\OTx{23}{x}{23x}{23x} \in \fOT{s_{23}}}^{x \in X}
-\end{align*}	
-\begin{align*}		
-		& \text{such that } \mpar{\forall x \in X, J'_{23x} \cap H' = J'_{13} \cap H'} \text{ and }\\
-		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \wedge\\[12pt]
-			 g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
-		\end{array}} 
-	\end{align*}
-Recall that by definition of composition and open automata refinement we have: 
-\begin{align*}
-&V_{13}= V_1\uplus V^1_3 \text{ and }
-V_{23}= V_2\uplus V^2_3\\
-& H' \subseteq J_3\uplus \mpar{J_1 \cap J_2} \setminus \{k\} = \mpar{J_3\uplus J_1 \setminus \{k\} } \cap \mpar{J_3\uplus J_2 \setminus \{k\}} \\
-\end{align*}
-First of all, we have by hypothesis $\wrel{A_1}{A_2}{H}$, then for any open transition $t_1$ in $T_1$  originating from $s_1$:
-\begin{align*}
-\OTx{1}{}{1}{1} \in \fOT{s_1}
-\end{align*}
-there exists an indexed family of OTs originating from $s_{2}$: 
-\begin{align*}
-\mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_{2}}}^{x \in X} 
-\end{align*}
-such that $\forall x \in X, J'_{2x} \cap H = J'_1 \cap H$ and
-\begin{multline*}
-%\everymath{\displaystyle}
-V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\ \mpar{R\mpar{s_1, s_{2}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \nwedge\\
-			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}}}  \qquad \quad (*)
-\end{multline*}	
-\smallskip
-
-Consider any transition $t_{13}$ in $A_{13}$.  Based on  the definition of composition $t_{13}$ can be obtained from two different cases, we will consider the two cases separately. 
-%\begin{enumerate}
-%\item 
-\paragraph{First case: Both automata perform a transition.}
-The transition $t_{13}$ is obtained by the composition of  transitions $t_1=\OTx{1}{}{1}{1}\in \fOT{s_1}$ and  \[t_3^1=
-\OT{ s^1_3}{{s^1_3}'}{\alpha_3^1}{   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{ g^1_3 }{ \psi^1_3}\in \fOT{s^1_3} \qquad \text{ when } k \in J'_{1} 
-\] The result is:
-\[
-t_{13} = \OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, {s^1_3}'}}{\alpha_1}{\beta_{1j}^{j \in J'_1 \setminus \{k\}} \uplus  {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{g_1 \wedge g^1_3 \wedge \alpha^1_3 = \beta_{1k}}{\psi_1 \uplus \psi^1_3} \qquad \text{ where } k \in J'_{1}
-\]
-We then obtain a family of OTs by the simulation of $A_1$ by $A_2$ (as stated above).
-By hypothesis we have $k \in H$, so in the case where $k \in J'_{1}$, we deduce that $k \in J'_{2x}$ we can  then build  a family of OTs $t_{23x}^{x\in X}$ with the same transitions of $A_3$ (up to renaming) as those used to build $t_{13}$.
-\[
-t_{23x} = \left(\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, {s^2_3}'}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }}{g_{2x} \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2xk}}{\psi_{2x} \uplus \psi^2_3}
-\right)^{x\in X}\]
-Recall that in this case  $k \in J'_{1}$, so $\forall x \in X$ we have
-\begin{align*}
-  J'_{23x} \cap H'  
-&=((J'_{2x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{3} ) \cap (H\uplus J_3 \setminus\{k\} )\\
-&=((J'_{2x}\cap (H\uplus J_3))\uplus (J^{2 \prime}_{3}\cap (H\uplus J_3)))\setminus \mbrc{k}\\
-&=((J'_{2x}\cap H)\uplus (J^{2 \prime}_{3}\cap  J_3))\setminus \mbrc{k}\text{ since } J_3\cap J'_{2x} = \emptyset \text{ and } H\cap J^{2 \prime}_{3} = \emptyset\\
-& =((J'_{2x}\cap H)\uplus J^{2 \prime}_{3})\setminus \mbrc{k}\text{ since } J^{2 \prime}_{3}\subseteq J_3\\
-& =((J'_1\cap H)\uplus J^{1 \prime}_{3})\setminus \mbrc{k}\quad \text{ since } J^{1 \prime}_{3}=J^{2 \prime}_{3} \text{ and } J'_1 \cap H = J'_{2x} \cap H\\
-&= ((J'_1 \cap H) \uplus (J^{1 \prime}_{3} \cap J_3)) \setminus \mbrc{k}\text{ since } J^{1 \prime}_{3}\subseteq J_3\\ 
-& = (J'_1\cap (J_3 \uplus H)) \uplus ((J^{1 \prime}_{3} \cap (J_3 \uplus H)) \setminus \mbrc{k} \text{ since } J_3\cap J'_{1} = \emptyset \text{ and } H\cap J^{1 \prime}_{3} = \emptyset\\
-		& = \mpar{(J'_1  \uplus J^{1 \prime}_{3})\setminus \mbrc{k}} \cap \mpar{(J_{3} \uplus H) \setminus \mbrc{k}}\\
-		& = J'_{13} \cap H'
-\end{align*}
-
-In this case the composition gives: \[g_{13} \Leftrightarrow g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k} \text{ and }
-g_{23x}  \Leftrightarrow g_{2x} \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk}\]
-As $k \in H$ we have   
-$\beta_{1k} = \beta_{2xk}$ then we  deduce:
-\[g^1_3 \wedge \alpha^1_3=\beta_{1k}  \Leftrightarrow g^2_3 \wedge \alpha^2_3= \beta_{2xk}\]
-The proof of the rest  is based on the following facts: 
-\begin{enumerate}
-\item  Because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.
-By construction of  $t_{13}$ and $t_{23}$ we have $\alpha_{13}=
-\alpha_{1}$ and $\alpha_{23x}=\alpha_{2x}$. So we deduce: 
-$\alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$.
-\item By composition we have also: \\ $\beta_{13j}^{j\in J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
-and $\beta_{23xj}^{j\in J'_{23}}= \beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }$\\
-Therefore, we have for all $j\in J'_{13}$ (recall that $J'_{13}=J'_{23}$):  \[\beta_{13j} = \beta_{23xj} \Rightarrow (j\in J_1 \land \beta_{1j} = \beta_{2xj}) \vee (j\in J_3^1 \land \beta^1_{3j}= \beta^2_{3j})\]
-\item 
-Considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up to renaming)  we have: \\
-${\displaystyle V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}} \vdash \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$\\
-The disjunction with the following hypothesis:\\ $V_{1} \uplus V_{2} \uplus \fvars{t_1}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}}$  will give:
-\begin{align*}
- V_{1} \uplus V_{2}  \uplus V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}}\vdash &    \bigwedge_\subbox{v_3\in V_3}\!\!
-v^1_3=v^2_3 \implies {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}} \vee {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}\\
-\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\!
-v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{2x}   \cap H)\uplus J^{2 \prime}_3 } \beta_{13j} = \beta_{23xj}} \\
-\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\!
-v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in \Rightarrow   ((J'_{2x}   \cap H)\uplus J^{2 \prime}_3)\setminus \{k\} } \beta_{13j} = \beta_{23xj}} \\
-\Rightarrow    V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\!
-v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{23x}   \cap H') } \beta_{13j} = \beta_{23xj}}
-\end{align*}
-\end{enumerate}
-
-By the extension of the valuation context mentioned above in the formula $(*)$ and by using the statements resulting from the cases (a), (b) and (c), we get:
-\begin{multline*}
-V_{13} \uplus V_{23}  \uplus \fvars{t_{13}} \vdash\\
-R\mpar{s_1, s_{2}} \wedge \mpar{g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}}\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3 %\wedge s^1_3=s^2_3
-\implies  \hspace{12em}\\
-\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in (J'_{23x} \cap H')} \beta_{13j}\! =\! \beta_{23xj}\\
-			 \nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}}  \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk} 
-%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
-\end{multline*}	
-That can be re-written as follows:
-\begin{multline*}
-V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
-R\mpar{s_1, s_{2}} \wedge g_{13}  \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3
-\implies  \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\
-			\nwedge g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}}   
-\end{multline*}
-
-Moreover, we have  for any transition $t_3$ in $A_3$ relying $s_3$ and $s^{\prime}_3$ the following:
-\begin{multline*}
-V_{13} \uplus V_{23}  \uplus \fvars{t_{13}} \vdash\\
-\bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3  \wedge s^1_3 = s^2_3 \implies \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3)  \wedge s^{1\prime}_3 = s^{2\prime}_3 
- \end{multline*}	
-From the two previous formulas, we get:
-\begin{multline*}
-V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
-R\mpar{s_1, s_{2}} \wedge g_{13}  \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3 \wedge s^1_3 = s^2_3
-\implies \hspace{7em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\land\\
-			  R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge
- \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3) \wedge s^{1\prime}_3 = s^{2\prime}_3
-		\end{array}}   
-\end{multline*}
-%And finally by hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,   by definition of reachability (Definition \ref{Def:Reach}) we obtain $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
-%\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
-%Thus, we get:
-%\begin{multline*}
-%V_{13} \uplus V_{23} \uplus  \fvars{t_{13}} \vdash\\
-%R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \reach{A_{13}}\mpar{s_{13}}
-%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
-%\implies \hspace{5em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-%\begin{array}{l}
-%			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge 	g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\\
-%		  \wedge \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
-%\wedge \bigwedge_\subbox{v_3\in V_3}  \psi_{13}(v^1_3)=\psi_{13}(v^2_3)\wedge s^{1\prime}_3=s^{2\prime}_3
-%		\end{array}}   
-%\end{multline*}	
-Because of the independence of the substitution domains, we simplify and get the expected formula:
-	\begin{multline*}
-  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ R^{\prime}\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
-			\nwedge g_{23x} \wedge R^{\prime}\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
-		\end{array}} 
-	\end{multline*}
-
-\smallskip
-
-\paragraph{Second case: Only the encompassing automaton performs a transition}
- $t_{13}$ is obtained  by  the transition $t_1=\OTx{1}{}{1}{1}$ alone with the state $s^1_3$ unchanged, if $k \not\in J_1'$
-\[t_{13} = \OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, s^1_3}}{\alpha_1}{\beta_{1j}^{j \in J'_1}}{g_1}{\psi_1}
-\]
-We then obtain a family of OTs by the simulation of $A_1$ by $A_2$ (stated above).
-As  $k \in H$ we have $k \not\in J'_{2x}$ and we build:
-\[t_{23x} = \left(
-\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, s^2_3}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x}}}{g_{2x}}{\psi_{2x}} \right)^{x\in X}\]
-
-These two cases define (depending on how $t_{13}$ is built) the family $t_{23x}$ of OTs we are looking for.
-Thus, for both cases we have to prove the following:
-\begin{align*}		
-		&\mpar{\forall x \in X, J'_{23x} \cap H' =
- J'_{13} \cap H'} \text{ and }\\
-		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ & R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
-			\nwedge g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
-		\end{array}} 
-	\end{align*}
-
-Recall in this case $k \notin J'_1$, $\forall x \in X$ we have
-\begin{align*}		
-J'_{23x} \cap H' & = J'_{2x}  \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
-& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
-& = \mpar{J'_1\cap H } \text{ since } J'_1 \cap H = J'_{2x} \cap H\\
-& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'
-\end{align*}
-
-The proof of the rest of the formula follows the same steps as the previous case the only argument that changes is that by composition we obtain:  $g_{13} \Leftrightarrow g_1$ and
-$g_{23x}  \Leftrightarrow g_{2x}$.\\
-
-\item The last formula we need to prove is that the relation is preserved along identical transitions, i.e.
-the following is satisfied (we define $V_{13} = V_1 \uplus V_3$ and $ V_{23} = V_2\uplus V_3$):
-
-\begin{multline*}
-\bigforall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}, \bigsymb{\forall} \mpar{t_{13}, t_{23}} = \mpar{\OTx{13}{}{13}{13}, \OTx{23}{}{23}{23}} \in \fOT{s_{13}} \times \fOT{s_{23}} \\ 
-\bigsymb{\bigexists} 
-\mpar{t_{13x} = \OTx{13}{x}{13x}{13x} \in \fOT{s_{13}}}^{x \in X},\\
- V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
-\vdash \hspace{6cm}\\  R\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
-\implies \\
-\bigsymb{\bigwedge_{x\in X}}
-\mpar{
- \alpha_{13}=\alpha_{1 3x} \land
-J'_{13x}  = J'_{23}  \land \bigwedge_\subbox{j \in  J'_{23}} \beta_{23j} = \beta_{13xj}\land g_{1 3x} \land
- R\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 3x} \uplus \psi_{23}}}
-\end{multline*}
-
-We pick $s_{13}$, $s'_{13a}$, and two open transitions $t_{13}$ and $t_{23}$.
-Where $s_{13}=(s_1,s_3)$ and $s_{23}=(s_2,s_3)$ by construction of $R'$.
-
-We reason on the way the open transition $t_{23}$ has been obtained: either the hole $k$ of $A_2$ is involved in the transition or not.
-
-\paragraph{First case: Both $A_2$ and $A_3$ are involved in transition $t_{23}$.}
-The transition $t_{23}$ is obtained by the composition of  transitions $t_2=\OTx{2}{}{2}{2}\in\fOT{s_2}$ and  \[t_3^2=
-\OT{ s_3}{{s^2_3}'}{\alpha_3^2}{   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }}{ g^2_3 }{ \psi^2_3}\in\fOT{s_3} \qquad \text{ when } k \in J'_{2} 
-\] The result is:
-\[
-t_{23} = \OT{\mpar{s_2, s_3}}{\mpar{s'_2, {s^2_3}'}}{\alpha_2}{\beta_{2j}^{j \in J'_2 \setminus \{k\}} \uplus  {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }}{g_2 \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k}}{\psi_2 \uplus \psi^2_3} \qquad \text{ where } k \in J'_{2}
-\]
-
-Two cases are possible for $t_{13}$: either the hole $k$ of $A_1$ is involved in the transition or not.
-
-$\bullet$ if  the hole $k$ of $A_1$ is involved in the transition: 
-The transition $t_{13}$ is obtained by the composition of  transitions $t_1=\OTx{1}{}{1}{1}\in\fOT{s_1}$ and  \[t_3^1=
-\OT{ s_3}{{s^1_3}'}{\alpha_3^1}{   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{ g^1_3 }{ \psi^1_3} \qquad \text{ when } k \in J'_{1} 
-\] The result is:
-\[
-t_{13} = \OT{\mpar{s_1, s_3}}{\mpar{s'_1, {s^1_3}'}}{\alpha_1}{\beta_{1j}^{j \in J'_1 \setminus \{k\}} \uplus  {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{g_1 \wedge g^1_3 \wedge \alpha^1_3 = \beta_{1k}}{\psi_1 \uplus \psi^1_3} \qquad \text{ where } k \in J'_{1}
-\]
-
-$\bullet$ if  the hole $k$ of $A_1$ is not involved in the transition:
-$t_1=\OTx{1}{}{1}{1}$ when  $k \not\in J'_{1} $
-and 
-\[
-t_{13} = \OT{\mpar{s_1, s_3}}{\mpar{s'_1, {s_3}}}{\alpha_1}{\beta_{1j}^{j \in J'_1}}{g_1}{\psi_1}
-\]
-
-\smallskip
-In both cases note that $g_{13} \implies g_1$, with  $\mpar{s_1, s_2} \in S_1 \times S_2$, Definition~\ref{def:preservation} applied to OTs $t_1,\,t_2$ gives the following property that we denote ($\star$):
-
-\begin{multline*}
-\bigexists 
-\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},\\
-  V_1 \uplus V_2 \uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 
-%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} 
-\implies \\
-\bigwedge_{x\in X}
-\mpar{
-\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_2 \land \bigwedge_\subbox{j \in J'_2 } \beta_{2j} = \beta_{1xj}\land g_{1 x}\land
- R\mpar{s'_{1 x}, s'_2}\psubst{\psi_{1 x} \uplus \psi_2}}
-\end{multline*}
-
-Consider one $t_{1x}=\OT{s_1}{s_{1x}}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x}}}{g_{1x}}{\psi_{1x}}\in \fOT{s_1}$ to obtain a new open transition of $A_{13}$ and compose it with $t_3^2$.
-We obtain 
-\[
-t_{13x}' = \OT{\mpar{s_1, s_3}}{\mpar{s_{1x}, {s_3}}}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x} \setminus \{k\}} \uplus  {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }}{g_{1x} \wedge g^2_3 \wedge \alpha^2_3 = \beta_{1xk}}{\psi_{1x} \uplus \psi^2_3} \qquad \text{ where } k \in J'_{1x}
-\]
-
-This specifies the family $\mpar{t_{13x}'}^{x\in X}$
-that allows us to prove the initial goal, i.e. the relation is preserved along identical transitions. We derive  from the definition of  $t_{23}$
-\begin{multline*}
-  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
-\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
-\implies \\
- R\mpar{s_{1}, s_{2}} \wedge 	g_{1} \wedge g_2 \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} \wedge \alpha_{1} = \alpha_{2} \wedge \bigwedge_\subbox{v_3\in V_3}
- v^1_3=v^2_3\wedge s^1_3 = s^2_3
-\end{multline*}
-Furthermore, from the property ($\star$) and from the definition of $t_{13x}'$:
-\begin{multline*}
-  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
-\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
-\implies 
-\bigwedge_{x\in X}
-\Big(
- \alpha_{13}=\alpha_1=\alpha_{1 x}  \land J'_{1x}\uplus J'_3= J'_2\uplus J'_3\land \\
-  \bigwedge_\subbox{j \in J'_2 \setminus\{k\} } \beta_{2j} = \beta_{1xj}
- \land \bigwedge_\subbox{j \in {j \in J^{2 \prime}_3} }  (\beta^1_{3j}) = (\beta^2_{3j}) \land g_{1 x}\land
- R\mpar{s'_{1x}, s'_{2}}\psubst{\psi_{1 x} \uplus \psi_2}\wedge \alpha^2_3 = \beta_{2k} = \beta_{1xk}\Big) \wedge g^2_3 \\
- \wedge \bigwedge_\subbox{v_3\in V_3}
- v^1_3=v^2_3\wedge s^1_3 = s^2_3
- \end{multline*}
-
-Finally, because $R'\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 x} \uplus \psi_2} \implies R'\mpar{s'_{1 3x}, s'_{23}}\psubst{(\psi_{1 x} \uplus \psi^2_3) \uplus (\psi_2 \uplus \psi^2_3)}$
-\begin{multline*}
-  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
-\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
-\implies \\
-\bigwedge_{x\in X}
-\mpar{
- \alpha_{13}=\alpha_{1 3x} \land
-J'_{13x}  = J'_{23}  \land \bigwedge_\subbox{j \in  J'_{23}} \beta_{23j} = \beta_{13xj}\land g_{1 3x} \land
- R'\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 3x} \uplus \psi_{23}}}
-\end{multline*}
-
-This concludes for the current case.
-
-\paragraph{Second case: Only $A_2$ is involved in transition $t_{23}$.}
-$t_{23}$ is obtained  by  the transition $t_2=\OTx{2}{}{2}{2}$ alone with the state $s^2_3$ unchanged, if $k \not\in J_2'$
-\[t_{23} = \OT{\mpar{s_2, s^2_3}}{\mpar{s'_2, s^2_3}}{\alpha_2}{\beta_{2j}^{j \in J'_2}}{g_2}{\psi_2}
-\]
-As in the previous case, two cases are possible for $t_{13}$: either the hole $k$ of $A_1$ is involved in the transition or not.
-
-$\bullet$ if  the hole $k$ of $A_1$ is involved in the transition: 
-The transition $t_{13}$ is obtained by the composition of  transitions $t_1=\OTx{1}{}{1}{1}\in\fOT{s_1}$ and  \[t_3^1=
-\OT{ s_3}{{s^1_3}'}{\alpha_3^1}{   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{ g^1_3 }{ \psi^1_3} \qquad \text{ when } k \in J'_{1} 
-\] The result is:
-\[
-t_{13} = \OT{\mpar{s_1, s_3}}{\mpar{s'_1, {s^1_3}'}}{\alpha_1}{\beta_{1j}^{j \in J'_1 \setminus \{k\}} \uplus  {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{g_1 \wedge g^1_3 \wedge \alpha^1_3 = \beta_{1k}}{\psi_1 \uplus \psi^1_3} \qquad \text{ where } k \in J'_{1}
-\]
-
-$\bullet$ if  the hole $k$ of $A_1$ is not involved in the transition:
-$t_1=\OTx{1}{}{1}{1}$ when  $k \not\in J'_{1} $
-and 
-\[
-t_{13} = \OT{\mpar{s_1, s_3}}{\mpar{s'_1, {s_3}}}{\alpha_1}{\beta_{1j}^{j \in J'_1}}{g_1}{\psi_1}
-\]
-
-In both cases note that $g_{13} \implies g_1$, with  $\mpar{s_1, s_2} \in S_1 \times S_2$, Definition~\ref{def:preservation} applied to OTs $t_1$ and $t_2$ gives the following property that we denote ($\star$):
-
-\begin{multline*}
-\bigexists 
-\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},\\
-  V_1 \uplus V_2 \uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 
-%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} 
-\implies \\
-\bigwedge_{x\in X}
-\mpar{
-\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_2 \land \bigwedge_\subbox{j \in J'_2 } \beta_{2j} = \beta_{1xj}\land g_{1 x}\land
- R\mpar{s'_{1 x}, s'_2}\psubst{\psi_{1 x} \uplus \psi_2}}
-\end{multline*}
-
-Consider one $t_{1x}=\OT{s_1}{s_{1x}}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x}}}{g_{1x}}{\psi_{1x}}\in \fOT{s_1}$ to obtain a new open transition of $A_1$    with the state $s^2_3$ unchanged, since $J'_{1x} = J_2'$ and $k \not\in J_2'$.
-
-We obtain 
-\[t_{13x}=\OT{(s_1,s^2_3)}{(s_{1x},s^2_3)}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x}}}{g_{1x}}{\psi_{1x}}\]
-In the same way this specifies the family, $\mpar{t_{13x}'}^{x\in X}$
-that allows us to prove the initial goal, i.e. the relation is preserved along identical transitions. We derive  from the definition of  $t_{23}$
-\begin{multline*}
-  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
-\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
-\implies \hspace{5cm}\\
- R\mpar{s_{1}, s_{2}} \wedge 	g_{1} \wedge g_2  \wedge \alpha_{1} = \alpha_{2} \wedge \bigwedge_\subbox{v_3\in V_3}
- v^1_3=v^2_3\wedge s^1_3 = s^2_3
-\end{multline*}
-
-And from the property ($\star$) and from the definition of $t_{13x}'$:
-\begin{multline*}
-  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
-\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
-\implies 
-\bigwedge_{x\in X}
-\Big(
- \alpha_{13}=\alpha_1=\alpha_{1 x}  \land J'_{1x}\uplus J'_3= J'_2\uplus J'_3\land \\
-  \bigwedge_\subbox{j \in J'_2  } \beta_{2j} = \beta_{1xj}
- \land \bigwedge_\subbox{j \in {j \in J^{2 \prime}_3} }  (\beta^1_{3j}) = (\beta^2_{3j}) \land g_{1 x}\land
- R\mpar{s'_{1x}, s'_{2}}\psubst{\psi_{1 x} \uplus \psi_2}\Big) 
- \wedge \bigwedge_\subbox{v_3\in V_3}
- v^1_3=v^2_3\wedge s^1_3 = s^2_3
- \end{multline*}
-
-%The proof continues as described above. \TODO{finish the proof}
-
-Which gives directly $R'\mpar{s'_{1 3x}, s'_{23}}$ as $A_3$ does not move (thus $\psi_{1 3x}=\psi_{1 x}$ and  $\psi_{23} =\psi_{2}$):
-\begin{multline*}
-  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
-\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
-\implies \\
-\bigwedge_{x\in X}
-\mpar{
- \alpha_{13}=\alpha_{1 3x} \land
-J'_{13x}  = J'_{23}  \land \bigwedge_\subbox{j \in  J'_{23}} \beta_{23j} = \beta_{13xj}\land g_{1 3x} \land
- R'\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 3x} \uplus \psi_{23}}}
-\end{multline*}
-
-This concludes for the second case and the proof of the theorem.
-
-\begin{comment}
- $\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$ and
-\begin{multline*}
- \bigsymb{\forall} \mpar{t_{13}, t_{23}} = \mpar{\OTx{13}{}{13}{13}, \OTx{23}{}{23}{23}} \in \fOT{s_{13}} \times \fOT{s_{23}} \\  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} \vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} \wedge \bigwedge_\subbox{j \in J'_{13} \cap J'_{23}} \beta_{13j} = \beta_{23j} \implies  R'\mpar{s'_{13}, s'_{23}}\psubst{\psi_{13} \uplus \psi_{23}}\\
-\end{multline*}
-
-Let's start  with the hypothesis of the theorem stating that $\wrel{A_1}{A_2}{H}$, thus we have   $\forall \mpar{s_1,s_{2}} \in S_1 \times S_2$ and
-\begin{multline*}
-\bigsymb{\forall} \mpar{t_1, t_{2}} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\  V_1 \uplus V_2 \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_{2} \wedge \alpha_1 = \alpha_{2} \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_{2}} \beta_{1j} = \beta_{2j} \implies  R\mpar{s'_1, s'_{2}}\psubst{\psi_1 \uplus \psi_2}
-\end{multline*}
-
-We have a second hypothesis stating that the result of the composition \(A_1\subst{A_3}{k}\) is non-blocking, by Definition \ref{Def:Non-blockcomp} we have:
-\begin{multline*}
-V_{13}  \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \left( \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \right)
-\end{multline*}
-
-Based on the definition of reachability of a state (Definition \ref{Def:Reach}) we have $\bigsymb{\forall} t_{13} = \OTx{13}{}{13}{13} \in T_{13}$
-\[\fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right)\]
-\begin{multline*}
-\vdash\\ \underbrace{R\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3}_{R^{\prime}(s_{13},s_{23})}  \wedge \dots \implies \ldots 
-\end{multline*}
-~~\\
-~~\\
-\TODO{Until here}
-The last formula we need to prove is the following: for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
-\begin{multline*}
-V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_{23}} \vdash \\ \left(R^{\prime}\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_1 \in \fOT{s_{13}}} \fguard{t_{13}} \right)
-\end{multline*}
-Let's start  with the hypothesis of the theorem stating that $\wrel{A_1}{A_2}{H}$, thus we have for all  $\mpar{s_1, s_2} \in S_1 \times S_2$ 
-\begin{multline*}
-V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
-\end{multline*}
-We extend the valuation to cover the variables of  $t^2_3$ in $t_{23}$ and using their value in $t_3$ and because the following statement holds: $\fvars{t_{13}} \vdash \reach{A_{13}}\mpar{s_{13}}$, we get:
-\begin{multline*}
-V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}  \wedge \reach{A_{13}}\mpar{s_{13}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}   \wedge \reach{A_{13}}\mpar{s_{13}}\right)
-\end{multline*}
-We have a second hypothesis stating that the result of the composition \(A_1\subst{A_3}{k}\) is non-blocking, by Definition \ref{Def:Non-blockcomp} we have:
-\begin{multline*}
-V_{13}  \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \left( \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \right)
-\end{multline*}
-By transitivity  we obtain:
-\begin{multline*}
-V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}   \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}\right)
-\end{multline*}
-
-Considering that each valuations $\sigma_{3}^1$ and $\sigma_{3}^2$ associate the same values to the ``same'' variables modulo renaming, so the following holds:\\ $\left(\,\,{\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{3}^1 \uplus \sigma_{3}^2 }$, we obtain:
-\begin{multline*}
-V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(\underbrace{R\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3}_{R^{\prime}(s_{13},s_{23})}  \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}   \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}\right)
-\end{multline*}
-which gives us what we needed to demonstrate. \qed
-% \end{enumerate}
-
-\end{comment}
-
-\end{enumerate}
+
 \end{document}
-
-\section{Proof of Congruence (Theorem~\ref{thm:Congruence})}
-
-Suppose that $\wrel{A_2}{A_3}{H}$, \(k \in H\) and that \(A_1\subst{A_2}{k}\) is non-blocking.
-We have: \[\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{J_1 \uplus H \setminus \mbrc{k}}\]
-\proof
-Let us denote by $A_{12}$ (resp.
-$A_{13}$) the open automaton resulting from $A_1\subst{A_2}{k}$ (resp.
-$A_1\subst{A_3}{k}$),  to prove the theorem it is sufficient to prove that there exists a relation between states of the two open automata that satisfies the conditions of the Definition \ref{Def:OA-Refinement}.
-We denote $A_1=  \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}$ and \(A_2 = \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and $A_3 = \OA{S_3}{s_{03}}{J_3}{V_3}{\sigma_{03}}{T_3}$.
-
-% The proof requires  to rename the variables of one instance of the two $A_3$ automata to avoid clashes in variable names (this is required by the definition of refinement).
-In practice we will use superscripts ${}^1$ and ${}^2$ to distinguish elements of the two instances of $A_3$.
-
-Let $R$ be the refinement relation relating states of $A_2$ and $A_3$. 
-Let us denote with $t^2$ and $t^3$  the elements of $A_2$ and $A_3$ respectively.
-Consider any two states $s_{12} = \mpar{s^1_1,s_2}$ and $s_{13} = \mpar{s^2_1,s_3}$ ($s^1_1$ and $s^2_1$  are the same with renaming).
-We define a relation $R'$ relating states of $s_{12}$ and $s_{13}$ as follows:
-\[ R' \mpar{s_{12}, s_{13}} = R\mpar{s_{2}, s_{2}} \wedge \reach{A_{12}}\mpar{s_{12}} \wedge \bigwedge_\subbox{v_1\in V_1}
- v^1_1=v^2_1\wedge s^1_1 = s^2_1\]
-Let us denote $H'=H\uplus J_1 \setminus\{k\}$.
-We want to prove that $\mpar{R', H'}$  is a hole-tracking simulation of $A_{12}$ and $A_{13}$. As for the previous proof we proceed by cases:
-\begin{enumerate}
-\item We have to prove that it holds for the initial configurations:
-\[\sigma_{012} \uplus \sigma_{013} \vdash R'\mpar{s_{012}, s_{013}}\]
-with $\sigma_{012} = \sigma_{01}^1 \uplus \sigma_{02}$, $\sigma_{013} = \sigma_{01}^2 \uplus \sigma_{03}$, $s_{012}=(s_{01}^1,s_{02})$, and $s_{013}=(s_{01}^2,s_{03})$.
-By using the fact that $R$ relates initial configurations of  $A_2$ and $A_3$, we have  the following statement:
-$\mpar{\sigma_{02} \uplus \sigma_{03} \vdash R\mpar{s_{02}, s_{03}}}$,  and based on the  fact that initial states are reachable $\sigma_{012} \vdash \reach{A_{12}}\mpar{s_{012}}$ we have:
-\[ \mpar{\sigma_{02} \uplus \sigma_{03} \vdash R\mpar{s_{02}, s_{03}}} \wedge 
-\mpar{\sigma_{012} \vdash \reach{A_{12}}\mpar{s_{012}}}\]
-Because initial valuations $\sigma_{01}^1$ and $\sigma_{01}^2$ associate the same values to the ``same'' variables modulo renaming, so the following holds:\\ $\left(\,\,{\displaystyle \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge s^1_1 = s^2_1}\right)\psubst{\sigma_{01}^1 \uplus \sigma_{01}^2 }$.
-
-Furthermore, because  the domains of the substitution function are disjoint, the substitution function has an effect only on the related elements,  we get:
-\begin{align*}
-& \mpar{\sigma_{02} \uplus \sigma_{03} \vdash R\mpar{s_{02}, s_{03}}} \wedge 
-\mpar{\sigma_{012} \vdash \reach{A_{12}}\mpar{s_{012}}}\\
-\implies & R\mpar{s_{02}, s_{03}}\psubst{ \sigma_{02} \uplus \sigma_{03}} \wedge \reach{A_{12}}\mpar{s_{012}} \psubst{\sigma_{012}} \land \mpar{\,\, {\displaystyle \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge s^1_1 = s^2_1}}\psubst{\sigma_{01}^1 \uplus \sigma_{01}^2 }\\
-\implies & \mpar{R\mpar{s_{02}, s_{03}} \wedge \reach{A_{12}}\mpar{s_{012}}  \wedge \bigwedge_\subbox{v_1\in V_1}  v^1_1=v^2_1\wedge s^1_1 = s^2_1} \psubst{ \sigma_{02} \uplus \sigma_{03} \uplus \sigma^1_{01}\uplus \sigma^2_{01} \uplus \sigma_{012}}\\
-\implies & \sigma_{012} \uplus \sigma_{013} \vdash R'\mpar{s_{012}, s_{013}}
-\end{align*}
-
-\item Second, we need to prove for any open transition $t_{12}$ in $T_{12}$ originating from $s_{12}$
-
-\begin{align*}
-		&  \OTx{12}{}{12}{12} \in \fOT{s_{12}}
-\end{align*}		
-there exists an indexed family $t_{13x}$ of OTs originating from $s_{13}$ that simulate it: 
-\begin{align*}
-		&  \mpar{\OTx{13}{x}{13x}{13x} \in \fOT{s_{13}}}^{x \in X}
-\end{align*}	
-such that  $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$ and
-\begin{multline*}	
-V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \wedge\\[12pt]
-			 g_{13x} \wedge R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
-		\end{array}} 
-	\end{multline*}
-By the definition of composition and open automata refinement we have: 
-\begin{align*}
-&V_{12}= V^1_1\uplus V_2 \text{ and }
-V_{13}= V^2_1\uplus V_3\\
-& H'=H_{23}\uplus J_1 \setminus \{k\} \subseteq J_1\uplus \mpar{J_2 \cap J_3} \setminus \{k\} = \mpar{J^1_1\uplus J_2 \setminus \{k\} } \cap \mpar{J^2_1\uplus J_3 \setminus \{k\}} = J_{12 } \cap J_{13} \\
-\end{align*}
-We have by hypothesis $\wrel{A_2}{A_3}{H}$, then for any open transition $t_2$ in $T_2$  originating from $s_2$:
-\begin{align*}
-\OTx{2}{}{2}{2} \in \fOT{s_2}
-\end{align*}
-there exists an indexed family of OTs originating from $s_{2}$: 
-\begin{align*}
-\mpar{\OTx{3}{x}{3x}{3x} \in \fOT{s_{3}}}^{x \in X} 
-\end{align*}
-such that $\forall x \in X, J'_{3x} \cap H = J'_2 \cap H$ and
-\begin{multline*}
-%\everymath{\displaystyle}
-V_2 \uplus V_3 \uplus \fvars{t_2} \vdash\\ \mpar{R\mpar{s_2, s_3} \wedge g_2 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_2 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj} \nwedge\\
-			 g_{3x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
-		\end{array}}}  \qquad \quad (*)
-\end{multline*}	
-\smallskip
-Consider any transition $t_{12}$ in $A_{12}$,  $t_{12}$ is obtained (by case analysis on the definition of composition).
-
-%\begin{enumerate}
-%\item 
-\paragraph{First case: Both automata perform a transition.} ~~\\
-The transition $t_{12}$ is obtained  by the composition of transitions $t_2=\OTx{2}{}{2}{2}$ and  \[t_1^1=
-\OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{   {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1} \qquad \text{ when } k \in {J^1_{1}}^{\prime}
-\]
-The result is the transition:
-\[
-t_{12} = \OT{\mpar{s^1_1, s_2}}{\mpar{{s^1_1}',s'_2 }}{\alpha^1_1}{{\beta^1_{1j}}^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {(\beta_{2j})^{j \in J^{\prime}_2} }}{g^1_1 \wedge g_2 \wedge \alpha_2 = \beta^1_{1k}}{\psi^1_1 \uplus \psi_2} \qquad \text{ where } k \in {J^1_{1}}^{\prime}
-\]
-
-We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (stated above).
-By hypothesis we have $k \in H$, so in the case where $k \in {J^1_{1}}^{\prime}$, we deduce that $k \in J'_{3x}$ we can  then build  a family of OTs $t_{13x}^{x\in X}$ with the same transitions of $A_1$ (up to renaming) as those used to build $t_{12}$.
-\[
-t_{13x} = \left(\OT{\mpar{s^2_1, s_3}}{\mpar{{s^2_{1}}',s'_{3x}}}{\alpha^2_{1}}  {{(\beta^2_{1j})^{{j \in J^{2 \prime}_1} \setminus \{k\}}}\uplus \beta_{3xj}^{j \in J'_{3x}  } }{ g^2_1 \wedge  g_{3x}  \wedge \alpha_{3x} =  \beta^2_{1k}}{\psi_{3x} \uplus \psi^2_1}
-\right)^{x\in X}\]
-Recall that in this case  $k \in {J^1_{1}}^{\prime}$
-\begin{align*}
-J'_{13} \cap H'  
-&=((J^{2 \prime}_{1} \uplus J'_{3x}) \setminus \mbrc{k}) \cap ((H\uplus J_1) \setminus\{k\} )\\
-& =((J^{2 \prime}_{1} \cap (H\uplus J_1)) \uplus (J'_{3x} \cap  (H\uplus J_1)))\setminus \mbrc{k}\\
-& =((J^{2 \prime}_{1} \cap  J_1)) \uplus (J'_{3x} \cap H))\setminus \mbrc{k}\text{ since }  J^{2 \prime}_{1}\cap H = \emptyset \text{ and } J'_{3x}\cap J_1 = \emptyset  \\
-& =(J^{2 \prime}_{1} \uplus (J'_{3x} \cap H))\setminus \mbrc{k} \text{ since } J^{1 \prime}_{1}\subseteq J_1\\
-& =(J^{1 \prime}_{1} \uplus (J'_{2} \cap H))\setminus \mbrc{k}  \text{ since } J^{1 \prime}_{1}=J^{2 \prime}_{1} \text{ and } J'_2 \cap H = J'_{3x} \cap H\\
-&  =((J^{1 \prime}_{1} \cap J_{1}) \uplus (J'_{2} \cap H))\setminus \mbrc{k} \text{ since } J^{1 \prime}_{1} \subseteq J_1 \\
-& = (J'_{2} \cap (J_1 \uplus H)) \uplus (J^{1 \prime}_{1}\cap (J_1 \uplus H))\setminus \mbrc{k} \text{ since } 
-J_1 \cap  J'_{2}= \emptyset \text{ and } H \cap J^{1 \prime}_{1} = \emptyset\\
-& = ((J'_{2} \uplus J^{1 \prime}_{1})\setminus \mbrc{k}) \cap   ((J_1 \uplus H)\setminus \mbrc{k})\\
-& = J'_{12}\cap H'
-\end{align*}
-In this case the composition gives:
-\[g_{12} \Leftrightarrow g^1_1 \wedge g_2 \wedge \alpha_2=\beta^1_{1k} \text{ and } g_{13x}  \Leftrightarrow g^2_1 \wedge  g_{3x}  \wedge \alpha_{3x}=\beta^2_{1k}\] 
-Furthermore, as $\beta^1_{1k} = \beta^2_{1k}$ then we get:
-\[ g^1_1  \wedge \alpha_2=\beta^1_{1k}  \Leftrightarrow g^2_1  \wedge \alpha_{3x}=\beta^2_{1k}\]
-As the previous case, the rest of the proof is based  on the fact:
-\begin{enumerate}
-\item The composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.
-By construction of  $t_{12}$ and $t_{13}$ we have $\alpha_{12}=
-\alpha^1_{1}$ and $\alpha_{13x}=\alpha^2_{1}$. As  $\alpha^1_{1}=\alpha^2_{1}$  we deduce: 
-$\alpha_{12} = \alpha_{13x}$. 
-\item By composition we have also:\\
- $\beta_{12j}^{j\in J'_{12}}= {({\beta^1_{1j}})^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {\beta_{2j}^{j \in J^{\prime}_2} }}$ and $\beta_{13xj}^{j\in J'_{13}}= {{(\beta^2_{1j})^{j \in {J^{2 \prime}_1} \setminus \{k\}}}\uplus \beta_{3xj}^{j \in J'_{3x} } }$
-
-Therefore, we have for all $j\in J'_{12}$ (recall that $J'_{12}=J'_{13}$):  
-\[\beta_{12j} = \beta_{13xj} \Rightarrow (j\in J^{1 \prime}_1 \land \beta^1_{1j}= \beta^2_{1j}) \vee  (j\in J'_2 \land \beta_{2j} = \beta_{3xj})  \]
-
-\item And considering $\beta^1_{1j}$ and  $\beta^2_{1j}$  are the same (up to renaming)  we have: 
-${\displaystyle V^1_{1} \uplus V^2_{1} \uplus \fvars{t_{1}} \vdash \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1\implies \bigwedge_\subbox{j \in J^{\prime}_1} \beta^1_{1j}= \beta^2_{1j}}$.
-
-Suppose that  $V_{2} \uplus V_{3} \uplus \fvars{t_{3x}}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj}}$ holds then we can deduce:
-\begin{align*}
-V^1_{1} \uplus V^2_{1} \uplus V_{2} \uplus V_{3} \uplus \fvars{t_{13x}}
-\vdash &   \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1\implies \bigwedge_\subbox{j \in J^{\prime}_1} \beta^1_{1j}= \beta^2_{1j} \vee  
-\bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj}\\
-\Rightarrow  V_{12} \uplus V_{13}  \uplus \fvars{t_{13x}}\vdash & 
-\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1
-\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{3x}   \cap H)\uplus J^{1 \prime}_1 } \beta_{12j} = \beta_{13xj}} \\  
-\Rightarrow   V_{12} \uplus V_{13}  \uplus \fvars{t_{13x}} \vdash & 
-\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1
-\implies 
-{\displaystyle \bigwedge_\subbox{j \in ((J'_{3x}   \cap H)\uplus J^{1 \prime}_1)\setminus \{k\} } \beta_{12j} = \beta_{13xj}}\\
-\Rightarrow  V_{12} \uplus V_{13}  \uplus \fvars{t_{13x}} \vdash & 
-\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1
-\implies 
-{\displaystyle \bigwedge_\subbox{j \in (J'_{13x}   \cap H')} \beta_{12j} = \beta_{13xj}}
-\end{align*}
-\end{enumerate}
-From the statements resulting the cases (a), (b) and (c),  and by  the formula $(*)$ we get:
-\begin{multline*}
-%\everymath{\displaystyle}
-V_2 \uplus V_3 \uplus \fvars{t_2} \vdash\\ R\mpar{s_2, s_3} \wedge g_2 \wedge  \mpar{g^1_1  \wedge \alpha_2=\beta^1_{1k}} \wedge \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1
-\implies\hspace{5em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge\\
-			 g_{3x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
-		\end{array}} \wedge    \mpar{g^2_1  \wedge \alpha_{3x}=\beta^2_{1k}}
-\end{multline*}	
-which can be simplified and re-written as follows:
-\begin{multline*}
-%\everymath{\displaystyle}
-V_{12} \uplus V_{13} \uplus \fvars{t_{13x}} \vdash\\ R\mpar{s_2, s_3} \wedge g_{12} \wedge \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1
-\implies\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge\\
-			 g_{13x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
-		\end{array}} 
-\end{multline*}	
-Furthermore, we have for any transition $t_1$ in $A_1$ relying $s_1$ and $s^{\prime}_1$ and for each $x \in X$ :
-\begin{multline*}
-V_{12} \uplus V_{13}  \uplus \fvars{t_{13x}} \vdash\\
-\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1  \wedge s^1_1 = s^2_1 \implies \bigwedge_\subbox{v_1\in V_1}\!\! \mpar{v^1_1=v^2_1} \psubst{\psi_{13x}} \wedge s^{1\prime}_1 = s^{2\prime}_1 
- \end{multline*}	
-We can deduce for all  $x \in X$ the following statement:
-\begin{multline*}
-V_{12} \uplus V_{13}  \uplus \fvars{t_{13x}} \vdash\\
-\bigwedge_\subbox{v_1\in V_1}\!\!
-v^1_1=v^2_1  \wedge s^1_1 = s^2_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\,\,\everymath{\displaystyle}\bigwedge_\subbox{v_1\in V_1}\!\!
-\mpar{v^1_1=v^2_1} \psubst{\psi_{13x}} \wedge s^{1\prime}_1 = s^{2\prime}_1 }
- \end{multline*}	
-Therefore, we get:
-\begin{multline*}
-%\everymath{\displaystyle}
-V_{12} \uplus V_{13} \uplus \fvars{t_{13x}} \vdash\\ R\mpar{s_2, s_3} \wedge g_{12} \wedge \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1 \wedge s^1_1 = s^2_1
-\implies \hspace{7em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge\\
-			 g_{13x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}} \wedge\bigwedge_\subbox{v_1\in V_1}\!\! \mpar{v^1_1=v^2_1} \psubst{\psi_{13x}} \wedge s^{1\prime}_1 = s^{2\prime}_1
-		\end{array}   } 
-		\end{multline*}
-
-From the hypothesis, we have \(A_1\subst{A_2}{k}\) is non-blocking.  Then, by definition of the reachability  (Definition \ref{Def:Reach}) we have  for all $t_{12} \in T_{12}$:
-\[ \fvars{t_{12}} \vdash \left(\reach{A_{12}}\mpar{s_{12}} \wedge g_{12} \implies \reach{A_{12}}\mpar{s_{12}'}\psubst{\psi_{12}}\right) \]	
-With the conjunction of the  formula obtained above and after simplifying, we get the expected result:
-\begin{multline*}	
-V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \wedge\\[12pt]
-			 g_{13x} \wedge R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
-		\end{array}} 
-	\end{multline*}
-
-\smallskip
-\paragraph{Second case: Only the encompassing automaton performs a transition.}~\\
-The transition $t_{12}$ is obtained  by  the transition $t_1^1=
-\OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{{(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1}$  alone with the state $s_2$ unchanged, if $k \not\in {J^1_{1}}^{\prime}$
-\[t_{12} = \OT{\mpar{s^1_1, s_2}}{\mpar{{s^1_1}', s_2}}{\alpha_1^1}{ {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{g^1_1}{\psi^1_1}
-\]
-We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (stated above).
-As  $k \in H$ we have $k \not\in J'_{3x}$ and we build with the same transitions of $A_1$ (up renaming):
-\[t_{13x} = \left(\OT{\mpar{s^2_1, s_3}}{\mpar{{s^2_1}', s_{3}}}{\alpha_1^2}{ {(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{g^2_1}{\psi^2_1} \right)^{x\in X}\]
-
-We have to  prove the following formula in both cases (depending on how the transition $t_{12}$ is built): $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$ and
-\begin{multline*}	
-V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \wedge\\[12pt]
-			 g_{13x} \wedge R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
-		\end{array}} 
-	\end{multline*}
-Recall in this case  $k \notin {J^1_{1}}^{\prime}$, so for all $x \in X$ we have:
-\begin{align*}
-	J'_{13x} \cap H' & = J'_{3x}  \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \\
-& = \mpar{J'_{3x}\cap H } \text{ since } J'_{3x}\cap J_1=\emptyset \land k\not\in J'_{3x} \\
-& = \mpar{J'_2\cap H } \text{ since } J'_2 \cap H = J'_{3x} \cap H\\
-& = \mpar{J'_{12}\cap H' } \text{ since } J_2\cap J'_1=\emptyset \land k\not\in {J^1_{1}}^{\prime}
-\end{align*}
-The proof of this case follows the same steps as the previous case the only argument that changes is that by composition we obtain:  $g_{12} \Leftrightarrow g^1_1$ and
-$g_{13x}  \Leftrightarrow g^1_{2}$.
-
-\item   It remains to prove the  satisfaction of the relation is preserved along identical transitions, i.e.
-the following is satisfied (we define $V_{12} = V_1 \uplus V_2$ and $ V_{23} = V_2\uplus V_3$):
-\begin{multline*}
-\forall \mpar{s_{12}, s_{13}} \in S_{12} \times S_{13}, \bigsymb{\forall} \mpar{t_{12}, t_{13}} = \mpar{\OTx{12}{}{12}{12}, \OTx{13}{}{13}{13}} \in \fOT{s_{12}} \times \fOT{s_{13}} \\ 
-\bigsymb{\bigexists} 
-\mpar{t_{12x} = \OTx{12}{x}{12x}{12x} \in \fOT{s_{12}}}^{x \in X},\\
- V_{12} \uplus V_{13} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{12}} \uplus \fvars{t_{13}} 
-\vdash \hspace{6cm}\\  R'\mpar{s_{12}, s_{13}} \wedge 	g_{12} \wedge g_{13} \wedge \alpha_{12} = \alpha_{13} 
-\implies \\
-\bigsymb{\bigwedge_{x\in X}}
-\mpar{
- \alpha_{12}=\alpha_{12x} \land
-J'_{12x}  = J'_{13}  \land \bigwedge_\subbox{j \in  J'_{13}} \beta_{13j} = \beta_{12xj}\land g_{12x} \land
- R'\mpar{s'_{12x}, s'_{13}}\psubst{\psi_{12x} \uplus \psi_{13}}}
-\end{multline*}
-
-We pick $s_{12}$, $s'_{12a}$, and two open transitions $t_{12}$ and $t_{13}$.
-Where $s_{12}=(s_1,s_2)$ and $s_{13}=(s_1,s_3)$ by construction of $R'$.
-
-We reason on the way the open transition $t_{13}$ has been obtained: either the hole $k$ of $A_1$ is involved in the transition or not.
-
-\paragraph{First case: Both $A_1$ and $A_3$ are involved in transition $t_{13}$.}
-The transition $t_{13}$  is obtained  by the composition of transitions $t_3=\OTx{3}{}{3}{3}$ and  \[t_1^1=
-\OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{   {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1} \qquad \text{ when } k \in {J^1_{1}}^{\prime}
-\]
-The result is the transition:
-\[
-t_{13} = \OT{\mpar{s^1_1, s_3}}{\mpar{{s^1_1}',s'_3 }}{\alpha^1_1}{{\beta^1_{1j}}^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {(\beta_{3j})^{j \in J^{\prime}_3} }}{g^1_1 \wedge g_3 \wedge \alpha_3 = \beta^1_{1k}}{\psi^1_1 \uplus \psi_3} \qquad \text{ where } k \in {J^1_{1}}^{\prime}
-\]
-
-According to the refinement relation between  $A_2$ and $A_3$ we have the following property that we denote $(*)$:
-\begin{multline*}
-\bigforall \mpar{s_2, s_3} \in S_1 \times S_3, \bigsymb{\forall} \mpar{t_2, t_3} = \mpar{\OTx{2}{}{2}{2}, \OTx{3}{}{3}{3}} \in \fOT{s_2} \times \fOT{s_3} \\ 
-\bigsymb{\bigexists} 
-\mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X},
-V_2 \uplus V_3\uplus \biguplus_{x\in X}\fvars{t_{2x}} \uplus \fvars{t_3} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R_{23}\mpar{s_2, s_3} \wedge 	g_2 \wedge g_3 \wedge \alpha_2 = \alpha_3 
-%\wedge \bigwedge_\subbox{j \in J'_2 \cap J'_3} \beta_{2j} = \beta_{3j} 
-\implies \hspace{6cm}\\
-%\exists
-%\OTx{1}{a}{3}{3}\in \fOT{s_2}. \\
-\bigsymb{\bigwedge_{x\in X}}
-\mpar{
-\alpha_2=\alpha_{2 x}  \land J'_{2x}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{2xj}\land g_{2 x}\land
- R\mpar{s'_{2 x}, s'_3}\psubst{\psi_{2 x} \uplus \psi_3}}\\
-\end{multline*}
-From the
-
-Consider any transition $t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}$ and compose it with  $t^1_1$. We get a family of  transitions:
-\[
-t_{12x}^{x\in X} = \mpar{\OT{\mpar{s^1_1, s_{2x}}}{\mpar{{s^1_1}',s'_{2x} }}{\alpha^1_1}{{\beta^1_{1j}}^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {(\beta_{2xj})^{j \in J^{\prime}_{2x}} }}{g^1_1 \wedge g_{2x} \wedge \alpha_{2x} = \beta^1_{1k}}{\psi^1_1 \uplus \psi_{2x}}}^{x\in X}  \quad \text{where } k \in {J^1_{1}}^{\prime}
-\]
-In order to prove the goal of of the expected relation let us start with the hypothesis:
-\begin{multline*}
-V_{12} \uplus V_{13} \uplus  \biguplus_{x\in X}\fvars{t_{2x}}  \uplus \fvars{t_{12}} \uplus \fvars{t_{13}} 
-\vdash \hspace{6cm}\\  R'\mpar{s_{12}, s_{13}} \wedge 	g_{12} \wedge g_{13} \wedge \alpha_{12} = \alpha_{13} 
-\implies  R\mpar{s_{2}, s_{3}}\wedge \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1 \wedge s^1_1 = s^2_1 \wedge \\
-g_1\wedge g^1_1 \wedge g_3 \wedge \alpha_3 = \beta^1_{1k} \wedge \alpha_2 = \alpha_3
-\end{multline*}
-From the property $(*)$ we get:
-
-\newpage
-
-for all $\mpar{s_{12}, s_{13}} \in S_{12} \times S_{13}$
-\begin{multline*}
-V_{12} \uplus V_{13} \uplus \biguplus_\subbox{t_{13}\in \fOT{s_{13}}} \fvars{t_{13}} \vdash \\ \left(R^{\prime}\mpar{s_{12}, s_{13}} \wedge \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \implies \bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}} \right)
-\end{multline*}
-
-Let's start with the hypothesis  stating that $\wrel{A_2}{A_3}{H}$, thus we have for all $\mpar{s_{2}, s_3} \in S_2 \times S_3$:
-\begin{multline*}
- V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash \left(R\mpar{s_{2}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \implies \bigvee_\subbox{t_{2p} \in \fOT{s_{2}}} \fguard{t_{2}} \right)
-\end{multline*}
-By adding the same term ${\displaystyle \reach{A_{12}}\mpar{s_{12}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}$ to both sides of the implication, we get:
-\begin{multline*}
- V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash\\ R\mpar{s_{2}, s_3} \wedge \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} \wedge \reach{A_{12}}\mpar{s_{12}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies\\ \bigvee_\subbox{t_{2p} \in \fOT{s_{2}}} \fguard{t_{2}} \wedge \reach{A_{12}}\mpar{s_{12}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
-\end{multline*}
-that can be re-written
-\begin{multline*}
- V_2 \uplus V_3 \uplus \biguplus_\subbox{t_3 \in \fOT{s_3}} \fvars{t_3} \vdash\\ R\mpar{s_{2}, s_3} \wedge \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \wedge \reach{A_{12}}\mpar{s_{12}}  \implies \bigvee_\subbox{t_{2} \in \fOT{s_{2}}} \fguard{t_{2}} \wedge \reach{A_{12}}\mpar{s_{12}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}
-\end{multline*}
-
-Yet we have by hypothesis  \(A_1\subst{A_2}{k}\) is non-blocking, by definition of non-blocking composition (Definition \ref{Def:Non-blockcomp}) we have:
-\begin{multline*}
- V_{12} \uplus  \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash
- \reach{A_{12}} \mpar{s_{12}}  \wedge  \bigvee_\subbox{t_{1} \in \fOT{s_{1}}} \fguard{t_{1}}  \implies \bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}
-\end{multline*}
-From the two previous formulas and considering that each valuations $\sigma_{1}^1$ and $\sigma_{1}^2$ associate the same values to the ``same'' variables modulo renaming we obtain the expected result.
-
-~\qed
-
- \end{enumerate}
-
-%\[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{J_3 \uplus H \setminus \mbrc{k}}\].
-
-\section{Proof that Composition is a refinement (Theorem~\ref{thm:Composition})}
-
-\section{Example}
-
-As an example, the traffic light system  that controls  
- traffic at an intersection. The open automaton  
-modeling this system  is illustrated in  Figure \ref{fig:tls}. This automaton has three states  remembering which coloured light
-is on (Red, Yellow or Green).
-It includes two holes: a controller ($\symb{ctl}$) and a counter ($\symb{cnt}$)  depicting together the behaviour of the timer.
-The color switches when the counter and the controller component agree that the time is over.
-The new time limit can be set by the counter component and the exposed action to the environment is an unobservable  action $\tau$.
-
-The open automata shown in Figure  \ref{fig:ctlandcnt} models  the timer.
-On the left, the controller component designed to be connected in the hole $\symb{ctl}$.
-Its role is to decide the duration before switching the lights.
-We control the time interval for each light by setting them by prior knowledge:  17s for the first duration, 3s for the second, and 20s for the third.
-On the right, the tick counter component designed to be connected in the hole $\symb{cnt}$.
-
-In Figure \ref{fig:tlf} we present the composition of the three automata.
-Each state of the result of the composition consists  of  a state of traffic light system together with a state of controller component and one of counter component.
-The composed automaton  takes over  the same steps as the traffic light automaton but it also includes new steps,  indicting the change of states for the setting of timer.
-Its $\tau$ transitions involve both the traffic light automaton and the hole  automata, they correspond to  a joint step of  sending time thresholds of the controller, the time setting of the counter.
-For instance, the  $\tau$  transition starting from \(R1S\), it is obtained by composition of both
-\nmm{\OT{R}{R}{\tau}{\mbrc{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}, \nmm{\OT{1}{2}{\theta\mpar{17}}{\mbrc{}}{\top}{\mbrc{}}} and   \nmm{\OT{S}{C}{\act{set}\mpar{x}}{\mbrc{}}{\top}{\mbrc{t \gets x, c \gets 0}}}.
-\\
-However, the joint composition of transitions  \nmm{\OT{R}{R}{\tau}{\mbrc{cnt \mapsto \act{set}\mpar{x}, ctl \mapsto \theta\mpar{x}}}{\top}{\mbrc{}}}, \nmm{\OT{2}{3}{\delta\mpar{x}}{\mbrc{}}{\top}{\mbrc{}}} and
-\nmm{\OT{C}{C}{\act{tick}}{\mbrc{}}{c < t}{\mbrc{c \gets c + 1}}} is not agreed because it would produce a transition whose guard is not satisfiable.
-It will produce the following transition: \nmm{\OT{R2C}{R3C}{\tau}{\mbrc{}}{\top \wedge \top \wedge c < t \wedge \act{set}\mpar{x} = \act{tick} \wedge \theta\mpar{x} = \delta\mpar{x}}{\mbrc{c \gets c + 1}}} which requires to be triggered  the equality of completely different actions.
-
-\begin{figure}[!tb]
-\centering
-\scalebox{.75}{\input{Traffic_Lights_Spec.tex}}
-\caption{The specification of a Traffic Light system}
-\label{fig:tls}
-\end{figure}
-
-\begin{figure}[!tb]
-%\centering
-\scalebox{.75}{\input{Traffic_Lights_Controller.tex}}
-\scalebox{.75}{\input{Traffic_Lights_Register.tex}}
-\caption{(a) An example of controller component ~~  (b) An example of counter component}
-\label{fig:ctlandcnt}
-\end{figure}
-
-\begin{figure}[!tb]
-\centering
-\scalebox{.75}{\input{Traffic_Lights_Interm.tex}}
-\caption{The incomplete Specification Traffic Lights system}
-\label{fig:tlf}
-\end{figure}
-
-\begin{figure}[!tb]
-\centering
-\scalebox{.75}{\input{Traffic_Lights_Full.tex}}
-\caption{The full Traffic Lights system}
-\label{fig:tlf}
-\end{figure}
-
-\end{document}

### 2022-11-30 2016-Weak-FH-Bisim/WeakBisim.tex
new figs

@@
 Each hole is represented by an empty disc, when the hole is filled it becomes a black disc.
-The left hole is indexed by $L$ and the right hole by $R$. The sub-net is a LTS with three states and emitting actions $l$ and $r$.
+The left hole is indexed by $L$ and the right hole by $R$.
+The sub-net is a LTS with three states and emitting actions $l$ and $r$.
+In the synchronisation vector $a$ and $b$ range over arbitrary action terms , e.g.
+including action parameters; $l$ and $r$ on the contrary are specific actions.
+The set of synchronisation vectors is  infinite but admits a simple finite representation.
 
@@
 \subsubsection*{Finite versus infinite open automata, and decidability} 
-As mentioned in Definition \pageref{def:open-automaton}, we adopt here a semantic view on open automata. More precisely, in \cite{hou:hal-02406098}, we  define
+As mentioned in page \ref{def:open-automaton}, we adopt here a semantic view on open automata. More precisely, in \cite{hou:hal-02406098}, we  define
 \emph{semantic open automata} (infinite as in Definition \ref{def:open-automaton}),
@@
 Let us point out that the weak OT loops ($WI_1$,$WI_2$ and $W_\tau$) on state ${000}$ are also present in all other states, we did not repeat them.
-Additionally, many WOTs are similar, and numbered accordingly as 3, 3a, 3b, 3c and 8, 8a, 8b, 8c respectively: they only differ by their respective source or target states; the "variant" WOTs appear in blue in   Figure~\ref{SimpleProtCounter:ImplWOA2}.
+Additionally, many WOTs are similar, and numbered accordingly as 3, 3a, 3b, 3c and 8, 8a, 8b, 8c respectively: they only differ by their respective source or target states; the "variant" WOTs appear in blue in   Figure~\ref{SimpleProtCounter:ImplWOA2}, note that composed WOTs also appear in blue.
 \end{example}
@@
 where $fv_{OT}$ denotes the set of free variables of all expressions in $OT$.
-\subsection{Weak FH-bisimilation for open pNets}
+\subsection{Weak FH-bisimulation for open pNets}
 

### 2022-12-15 2021-Refinement/paper/refinementarticleV2.tex
new refinement
work on refinement
V2

@@
 \usepackage{comment}
+\usepackage{macrospNets}
 
@@
 
-\DeclareMathOperator{\dom}{dom}
-\newcommand{\rightarrowdbl}{\rightarrow\mathrel{\mkern-14mu}\rightarrow}
+%\DeclareMathOperator{\dom}{dom}
+%\newcommand{\rightarrowdbl}{\rightarrow\mathrel{\mkern-14mu}\rightarrow}
 
@@
 
-\newcommand{\symb}[1]{\makebox{\it #1}}
+%\newcommand{\symb}[1]{\makebox{\it #1}}
 \input{common.tex}
@@
 \input{tikzmacros.tex}
+%\input{macrospNets.sty}
 
@@
 \noindent\begin{multline*}
-\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_2} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\ 
+ \bigsymb{\forall} {t_1} = \openrule
+         {
+           \beta_{1 j}^{j\in J}, g_1,\psi_1}
+         {s_1 \OTarrow {\alpha_1} s_1'} \in \fOT{s_1} .\,~~
+\bigsymb{\bigexists} 
+\mpar{t_{2x} \!=\! \openrule
+         {
+           \beta_{2 x j}^{j\in J}, g_{2 x},\psi_{2 x}}
+         {s_2 \OTarrow {\alpha_{2 x}} s_{2 x}'}
+}^{x \in X}\in \fOT{s_2}.\,~~\\ 
 \everymath{\displaystyle}\begin{array}{l}
-V_1 \uplus V_2 \uplus \fvars{t_1} \uplus \fvars{t_2}  \vdash R\mpar{s_1, s_2} \wedge g_2 \implies\\
-V_1 \uplus V_2 \uplus \fvars{t_{1x}} \uplus \fvars{t_2}\vdash  \bigsymb{\bigexists} 
-\mpar{t_{1x} \!=\! \OTx{1}{x}{1x}{1x}}^{x \in X} \operatorname*{\bigsymb{\bigvee}}_{x \in X}
+V_1 \uplus V_2 \uplus  \fvars{t_1} \uplus \bigcup_x\fvars{t_{2x}}  \vdash
+\\
+ R\mpar{s_1, s_2} \wedge g_1 \implies
+ \operatorname*{\bigsymb{\bigvee}}_{x \in X}
 \mpar{\begin{array}{l}
-			\alpha_{1x} = \alpha_{2} \wedge \bigwedge_\subbox{j \in J'_{2}} \beta_{1xj} = \beta_{2j} \nwedge\\[12pt]
-			 g_{1x} \wedge R\mpar{s'_{1x}, s'_{2}}\psubst{\psi_{1x} \uplus \psi_{2}}
+			\alpha_{2x} = \alpha_{1} \wedge \bigwedge_\subbox{j \in J} \beta_{2xj} = \beta_{1j} \nwedge\\[12pt]
+			 g_{2x} \wedge R\mpar{ s'_{1},s'_{2x}}\psubst{\psi_{2x} \uplus \psi_{1}}
 		\end{array}} 
@@
 \begin{multline*}
-\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge  \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}
+\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \wedge \lnot( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )\implies \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
 \end{multline*}
@@
 
-%\section{a recuperer si on se rend compte que c'est utile}
-%When we will introduce refinements in Section \ref{sec:prelref}, setting an undefined variable will be considered a valid refinement, for instance a \(5\) bits register is a particular \(n\) bits register.
-
 \newpage
@@
 \section{Proof of Transitivity for Refinement}\label{sec:proof-transitivity}
+\begin{quote}
+If $\wrel{A_1}{A_2}{H}$ and $\wrel{A_2}{A_3}{H'}$, then $\wrel{A_1}{A_3}{H\cap H'}$.
+\end{quote}
+\proof 
+If $\wrel{A_1}{A_2}{H}$ then there is $R_{12}$ a relation between states
+of $A_1$ and of $A_2$;  If $\wrel{A_2}{A_3}{H'}$ then there is $R_{23}$ a relation between states of $A_2$ and of $A_3$. We build a relation between
+ states of $A_1$ and of $A_3$ as follows:  for each pair of states $s_1$, $s_3$, for each state $s_2$ such that $R_{12}$ relates $s_1$ and $s_2$, and $R_{23}$ relates $s_2$ and $s_3$.
+Let $R_{13}$ be the relation:\\
+  \[R_{13}(s_1,s_3)=\bigvee_{s_2\in S_2}\mpar{R_{12}(s_1,s_2) \land R_{23}(s_2,s_3) } \]
+
+We will show that $\wrel{A_1}{A_3}{H\cap H'}$ by exhibiting  $R_{13}$ as a hole-tracking simulation of $A_1$ by  $A_3$.
+
+We have to prove that the relation $R_{13}$ satisfies the three conditions of the definition of a refinement of open automata.
+\begin{enumerate}
+\item Firstly, we have to $R_{13}$ satisfies initial configurations:
+\[\sigma_{01} \uplus \sigma_{03} \vdash R_{13} \mpar{s_{01}, s_{03}}\]
+By knowing that substitutions only have an effect on the variables of the open automaton they belong to, they also produce terms containing only variables of the open automaton they belong to.
+We have:
+\begin{align*}
+\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar
+{\sigma_{02} \uplus \sigma_{03} \vdash R_{23}\mpar{s_{02}, s_{03}}}&\implies\\
+R_{12}\mpar{s_{01},s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02}} \wedge R_{23}\mpar{s_{02}, s_{03}}\psubst{\sigma_{02} \uplus \sigma_{03}}&\implies\\
+R_{12}\mpar{s_{01},s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} \wedge R_{23}\mpar{s_{02}, s_{03}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}}&\implies\\ 
+\underbrace{R_{12}\mpar{s_{01},s_{02}}\wedge R_{23}\mpar{s_{02}, s_{03}}}_{\implies R_{13} \mpar{s_{01}, s_{03}}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} %&\implies\\
+ \end{align*}
+Since $\sigma_{02}$ has no effect on variables of $s_{01}$ and $s_{03}$ thus we get the expected result.
+
+\item \TODO{Ref to JLAMP 2023?}
+
+\item Lastly, we have to prove the satisfaction of the deadlock reduction condition:
+According to the relation between A2 and A3 we have for all
+
+%\begin{multline*}
+%\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \wedge \lnot( %\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )\implies \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} %\fguard{t_2}  )
+%\end{multline*}
+
+\end{enumerate}
+%\section{a recuperer si on se rend compte que c'est utile}
+%When we will introduce refinements in Section \ref{sec:prelref}, setting an undefined variable will be considered a valid refinement, for instance a \(5\) bits register is a particular \(n\) bits register.
+
+\section{Proof of Transitivity for Refinement}\label{sec:proof-transitivity}
 

### 2022-12-15 2021-Refinement/paper/refinementarticleV2.tex
reformulation

@@
 \begin{definition}[Hole-equal simulation]
-Consider two OA with identical set of holes:  \(\OAg[1]\) and \(\OAg[2]\) where  \(J_1 = J_2\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $S_1$ to $S_2$ if the following conditions hold:
+Consider two OA with identical set of holes:  \(\OAg[1]\) and \(\OAg[2]\) where  \(J_1 = J_2\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $S_1$ to $S_2$ if the following conditions hold (we could denote it $T_1\leq T_2$):
 \item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
@@
 \forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \wedge \lnot( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )\implies \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
+\end{multline*}
+
+Which can be rewritten as:
+\begin{multline*}
+\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
 \end{multline*}

### 2022-12-20 2021-Refinement/paper/refinementarticleV2.tex
refine
current version

@@
 \begin{multline*}
-\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
+\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
 \end{multline*}
@@
 
-\item Lastly, we have to prove the satisfaction of the deadlock reduction condition:
-According to the relation between A2 and A3 we have for all
+\item Lastly, we have to prove the satisfaction of the deadlock reduction condition. According to the relation between A2 and A3 we have for all $\mpar{s_{2p},s_3} \in S_2\times S_3$
+\begin{multline*}
+ V_2 \uplus V_3  \vdash R\mpar{s_{2p},s_3} \implies ( \bigvee_\subbox{t_1 \in \fOT{s_{2p}}} \fguard{t_{2p}} ) \lor¢ \lnot( \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} )
+\end{multline*}
 
-%\begin{multline*}
-%\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \wedge \lnot( %\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )\implies \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} %\fguard{t_2}  )
-%\end{multline*}
+\begin{multline*}
+\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
+\end{multline*}
+
+\begin{multline*}
+\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \wedge \lnot( %\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )\implies \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} %\fguard{t_2}  )
+\end{multline*}
 
@@
 
-\section{Proof of Transitivity for Refinement}\label{sec:proof-transitivity}
+%\section{Proof of Transitivity for Refinement}\label{sec:proof-transitivity}
 

### 2023-01-06 2021-Refinement/paper/refinementarticleV2.tex
suite preuve

@@
 \begin{definition}[Hole-equal simulation]
-Consider two OA with identical set of holes:  \(\OAg[1]\) and \(\OAg[2]\) where  \(J_1 = J_2\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $S_1$ to $S_2$ if the following conditions hold (we could denote it $T_1\leq T_2$):
+Consider two OA with identical set of holes:  \(\OAg[1]\) and \(\OAg[2]\) where  \(J_1 = J_2\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $S_1$ to $S_2$ if the following conditions hold (we could denote it $A_1\leq A_2$):
 \item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
@@
 \everymath{\displaystyle}\begin{array}{l}
-V_1 \uplus V_2 \uplus  \fvars{t_1} \uplus \bigcup_x\fvars{t_{2x}}  \vdash
+V_1 \uplus V_2 \uplus  \fvars{t_1} \uplus \bigcup_x\fvars{t_{2x}}  \vdash \hspace{7cm}
 \\
@@
 
-\item Lastly, we have to prove the satisfaction of the deadlock reduction condition. According to the relation between A2 and A3 we have for all $\mpar{s_{2p},s_3} \in S_2\times S_3$
+\item Lastly, we have to prove the satisfaction of the deadlock reduction condition. 
+ To build $R_{13}$ we need to rely on the disjunction of all possible paths to relate $s_1$ and $s_3$, which leads to \[{\displaystyle R_{13}(s_1,s_3)=\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}}\]
+
+Consider any $\mpar{s_{1}, s_{3}} \in R_{13}$  there is a set of states $(s_{2p})^{p\in P}$ of $A_2$ relating  $s_{1}$ and $s_{3}$.
+
+First, according to the relation between $A_1$ and $A_2$ open automata,  for all $\mpar{s_1, s_{2p}} \in S_1\times S_2$  we have:
 \begin{multline*}
- V_2 \uplus V_3  \vdash R\mpar{s_{2p},s_3} \implies ( \bigvee_\subbox{t_1 \in \fOT{s_{2p}}} \fguard{t_{2p}} ) \lor¢ \lnot( \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} )
+%\forall \mpar{s_1, s_{2p}} \in S_1 \times S_2, 
+V_1 \uplus V_2  \vdash R_{12}\mpar{s_1, s_{2p}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}  \lor¢ \lnot( \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}}  )
+\end{multline*}
+Second, according to the relation between $A_2$ and $A_3$ open automata, for all $\mpar{s_{2p},s_3} \in S_2\times S_3$  we have:
+\begin{multline*}
+ V_2 \uplus V_3  \vdash R_{23}\mpar{s_{2p},s_3} \implies  \bigvee_\subbox{t_1 \in \fOT{s_{2p}}} \fguard{t_{2p}}  \lor¢ \lnot( \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} )
+\end{multline*}
+With the conjunction of both, we get:
+
+\begin{multline*}
+ V_1 \uplus V_2 \uplus V_3  \vdash  R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \implies   \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} 
+ \lor¢ \lnot( \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} )
 \end{multline*}
 
+This is valid for all $s_{2p} \in (s_{2p})^{p\in P}$, then we have:
 \begin{multline*}
-\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
+ V_1 \uplus V_2 \uplus V_3  \vdash \underbrace{\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}}_{R_{13}(s_1,s_3)} \implies  ( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )
+ \lor¢ \lnot( \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} )
 \end{multline*}
+By removing the $A_2$ variables that have not effect on $A_2$ et $A_3$,
+we get the desired result:
+\begin{multline*}
+ V_1 \uplus  V_3  \vdash R_{13}(s_1,s_3) \implies  ( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )
+ \lor¢ \lnot( \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} )
+\end{multline*}
+\qed
+\section{Proof of Context Refinement (Theorem~\ref{thm:ContextRefinement})}
 
+\begin{quote}
+Suppose 
+\end{quote}
+
+\proof
+Let us denote by $A_{13}$ (resp.
+$A_{23}$) the open automaton resulting from $A_1\subst{A_3}{k}$ (resp.
+$A_2\subst{A_3}{k}$),  to prove the theorem it is sufficient to prove that there exists a relation between states of the two open automata that satisfies the conditions of the Definition \ref{Def:OA-Refinement}.
+
+We denote $A_1=  \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}$ and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and $A_3 = \OA{S_3}{s_{03}}{J_3}{V_3}{\sigma_{03}}{T_3}$.
+The proof requires  to rename the variables of one instance of the two $A_3$ automata to avoid clashes in variable names (this is required by the definition of refinement).
+In practice we will use superscripts ${}^1$ and ${}^2$ to distinguish elements of the two instances of $A_3$.
+
+Let $R$ be the refinement relation relating states of $A_1$ and $A_2$. 
+Let us denote with $t^1$ and $t^2$  the elements of $A_1$ and $A_2$ respectively.
+Consider any two states $s_{13} = \mpar{s_1,s^1_3}$ and $s_{23} = \mpar{s_2,s^2_3}$ ($s^1_3$ and $s^2_3$  are the same with renaming).
+We define a relation $R'$ relating states of $s_{13}$ and $s_{23}$ as follows:
+\[ R' \mpar{s_{13}, s_{23}} = R\mpar{s_{1}, s_{2}}  %\wedge \reach{A_{13}}\mpar{s_{13}}
+ \wedge \bigwedge_\subbox{v_3\in V_3}
+ v^1_3=v^2_3\wedge s^1_3 = s^2_3\]
+
+%\TODO{[Ludo] I believe reachability is not useful here -- to check}
+
+We want to prove that $\mpar{R', H\uplus J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$. In the following we denote $H'=H\cup J_3 \setminus\{k\}$.
+\begin{enumerate}
+\item First, we have to prove the relation for initial states:
+\[\sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}\]
+with $\sigma_{013} = \sigma_{01} \uplus \sigma_{03}^1$, $\sigma_{023} = \sigma_{02} \uplus \sigma_{03}^2$, $s_{013}=(s_{01},s_{03}^1)$, and $s_{023}=(s_{02},s_{02}^2)$.\\
+By using the fact that $R$ relates initial configurations of  $A_1$ and $A_2$, we have:
+$\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}}$.  
+%and based on the  fact that initial states are reachable $\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ we have 
+%\[ \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
+%\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\]
+
+Considering that initial valuations $\sigma_{03}^1$ and $\sigma_{03}^2$ associate the same values to the ``same'' variables modulo renaming, so the following holds:\\ $\left(\,\,{\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }$.
+
+Additionally, because  the domains of the substitution function are disjoint, the substitution function has an effect only on the related elements,  we get:
+\begin{align*}
+& \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} 
+%\wedge \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}
+\\
+\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}}  \land \mpar{\,\,\bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }\\
+\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge  \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma^1_{03}\uplus \sigma^2_{03}\uplus \sigma_{013} }\\
+\implies & \sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}
+\end{align*}
+\item Second, we need to prove for any open transition $t_{13}$ in $T_{13}$ originating from $s_{13}$:
+\begin{align*}
+		&  \OTx{13}{}{13}{13} \in \fOT{s_{13}}
+\end{align*}		
+there exists an indexed family $t_{23x}$ of OTs originating from $s_{23}$ that simulate it: 
+\begin{align*}
+		&  \mpar{\OTx{23}{x}{23x}{23x} \in \fOT{s_{23}}}^{x \in X}
+\end{align*}	
+\begin{align*}		
+		& \text{such that } \mpar{\forall x \in X, J'_{23x} \cap H' = J'_{13} \cap H'} \text{ and }\\
+		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \wedge\\[12pt]
+			 g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
+		\end{array}} 
+	\end{align*}
+Recall that by definition of composition and open automata refinement we have: 
+\begin{align*}
+&V_{13}= V_1\uplus V^1_3 \text{ and }
+V_{23}= V_2\uplus V^2_3\\
+& H' \subseteq J_3\uplus \mpar{J_1 \cap J_2} \setminus \{k\} = \mpar{J_3\uplus J_1 \setminus \{k\} } \cap \mpar{J_3\uplus J_2 \setminus \{k\}} \\
+\end{align*}
+First of all, we have by hypothesis $\wrel{A_1}{A_2}{H}$, then for any open transition $t_1$ in $T_1$  originating from $s_1$:
+\begin{align*}
+\OTx{1}{}{1}{1} \in \fOT{s_1}
+\end{align*}
+there exists an indexed family of OTs originating from $s_{2}$: 
+\begin{align*}
+\mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_{2}}}^{x \in X} 
+\end{align*}
+such that $\forall x \in X, J'_{2x} \cap H = J'_1 \cap H$ and
 \begin{multline*}
-\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \wedge \lnot( %\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )\implies \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} %\fguard{t_2}  )
+%\everymath{\displaystyle}
+V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\ \mpar{R\mpar{s_1, s_{2}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \nwedge\\
+			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}}}  \qquad \quad (*)
 \end{multline*}	
+\smallskip
+
+Consider any transition $t_{13}$ in $A_{13}$.  Based on  the definition of composition $t_{13}$ can be obtained from two different cases, we will consider the two cases separately.
+
+\end{enumerate}
 

### 2023-01-09 2021-Refinement/paper/refinementarticleV2.tex
version complete

@@
 
+\TODO{Je reintroduis la notion de reachability et non introduction de blocage}
+\subsection{Deadlock Reduction, Reachability, and Composition}
+
+A notion that is often used in the context of refinement is the notion of deadlock reduction.
+This property considers that two states related by a given relation and states that if one state can do a transition, then the other can do a transition too.
+This notion is not much interesting in the general case as there is a priori no relation between the two transitions.
+However, when the relation that relates states is a simulation, this will relate the possible transitions and the deadlock reduction will become a valuable property.
+
+Next definition states that if $T_2$ is not in a deadlock position then $T_1$ can do a transition but not necessarily with the same input values.
+This is very weak but sufficient when composed with the def  of simulation.
+
+\begin{definition}[Deadlock reduction]\label{def:dpwd}\\
+Let \(\OAg[1]\) and \(\OAg[2]\) be two OAs.
+A relation on OA configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is deadlock reducing if  it satisfies the following\footnote{Note that variables of $T_1$ are existentially quantified in the proposition.}:
+\begin{multline*}
+ \forall \mpar{s_1, s_2} \in S_1 \times S_2,\\ V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
+\end{multline*}
+\end{definition}
+
+Because of the symbolic nature of OAs and their structure, in this definition,  the fact that a guard is true is sufficient to reason on the possible paths.
+This slightly simplifies the definition and makes the characterisation of transition that can be triggered very symbolic.
+An equivalent but more classical definition of deadlock reduction could be expressed as well.
+It states that if there is a transition that can be triggered in the first automaton, then there is a transition from the related state in the second automaton that can be triggered.
+This second definition is more verbose, in particular because of the multiple quantifiers over transitions and automaton state.
+The alternative definition is equivalent to this one when reasoning on a refinement relation (but not in general).
+
+Unfortunately, this property is not compositional: the composition operator can itself introduce a deadlock.
+In other words, when filling the hole of two related automata with a third one, even if there is a deadlock reduction between the two original automata , there might not be a deadlock reduction in the composed ones.
+The same problem may arise when two related automata are composed in the same hole of a third one.
+
+This creates a conflict between deadlock reduction and the properties involving composition.
+One possible solution to avoid this conflict is to only consider a composition that do not introduce deadlocks, we will define such a composition below.
+But before defining non-blocking composition, we first introduce a notion of state reachability for open automata. 
+\begin{definition}[Reachability] \label{Def:Reach}
+For any open automata \(A = \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is any predicate on states that is valid on initial state, and preserved across transitions:
+\[\sigma_0 \vdash \reach{A}\mpar{s_0}\quad\land\quad\forall t = \OTg \in T, \fvars{t} \vdash \left(\reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}\right)\]
+\end{definition}
+Reachability takes into account all paths, and can over-approximate the reachable configurations. 
+From an automation point of view, finding the most precise reachability predicate for a given automata is not decidable because of the symbolic nature of open automata, but only an over-approximation is necessary.
+An automatic tool would only need to find an over approximation of reachability to reason on composition that is compatible with deadlock reduction.
+We call \emph{non-blocking composition} a composition that can be safely be used to compose open automata that are involved in a deadlock reducing relation.
+
+\begin{definition}[Non-blocking composition]
+Let \(A_i = \OAg[i]\) with \( 0 \leq i \leq n\) be a family of open automata.
+Let \(A = A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) and $A= \OAg$.
+
+The composition \(A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is non-blocking if   \(A \) has a reachability predicate such that, for each reachable configuration, if there is a possible transition in \(A_0\) then there is a possible transition in \(A\):
+\[ \forall s = \mpar{s_0, s_1,..,s_n} \in S, V \uplus \biguplus_\subbox{t_0 \in \fOT{s_0}} \fvars{t_0} \vdash \left(\reach{A}\mpar{s} \wedge \bigvee_\subbox{t_0 \in \fOT{s_0}} \fguard{t_0} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \right)\]
+\end{definition}
+Again we use guards to ensure that the transition can occur. It is not sufficient to ensure the existence of equivalent transitions in general, but it will be sufficient in the context of refinement.
+
+\TODO{Fin reintrod.}
+
 The major challenge in the design of this relation is to maintain a form of transitivity while being able to take into account the actions of some of the holes.
@@
 \qed
+\end{enumerate}
 \section{Proof of Context Refinement (Theorem~\ref{thm:ContextRefinement})}
-
 \begin{quote}
-Suppose 
+Suppose that $\wrel{A_1}{A_2}{H}$, \(k \in H\) and that \(A_1\subst{A_3}{k}\) is non-blocking. We have: 
+\[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{J_3 \uplus H \setminus \mbrc{k}}\]
 \end{quote}
+\smallskip
 
@@
 		& \text{such that } \mpar{\forall x \in X, J'_{23x} \cap H' = J'_{13} \cap H'} \text{ and }\\
-		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\
+		& R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
 			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \wedge\\[12pt]
@@
 
+\paragraph{First case: Both automata perform a transition.}
+The transition $t_{13}$ is obtained by the composition of  transitions $t_1=\OTx{1}{}{1}{1}\in \fOT{s_1}$ and  \[t_3^1=
+\OT{ s^1_3}{{s^1_3}'}{\alpha_3^1}{   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{ g^1_3 }{ \psi^1_3}\in \fOT{s^1_3} \qquad \text{ when } k \in J'_{1} 
+\] The result is:
+\[
+t_{13} = \OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, {s^1_3}'}}{\alpha_1}{\beta_{1j}^{j \in J'_1 \setminus \{k\}} \uplus  {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{g_1 \wedge g^1_3 \wedge \alpha^1_3 = \beta_{1k}}{\psi_1 \uplus \psi^1_3} \qquad \text{ where } k \in J'_{1}
+\]
+We then obtain a family of OTs by the simulation of $A_1$ by $A_2$ (as stated above).
+By hypothesis we have $k \in H$, so in the case where $k \in J'_{1}$, we deduce that $k \in J'_{2x}$ we can  then build  a family of OTs $t_{23x}^{x\in X}$ with the same transitions of $A_3$ (up to renaming) as those used to build $t_{13}$.
+\[
+t_{23x} = \left(\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, {s^2_3}'}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }}{g_{2x} \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2xk}}{\psi_{2x} \uplus \psi^2_3}
+\right)^{x\in X}\]
+Recall that in this case  $k \in J'_{1}$, so $\forall x \in X$ we have
+\begin{align*}
+  J'_{23x} \cap H'  
+&=((J'_{2x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{3} ) \cap (H\uplus J_3 \setminus\{k\} )\\
+&=((J'_{2x}\cap (H\uplus J_3))\uplus (J^{2 \prime}_{3}\cap (H\uplus J_3)))\setminus \mbrc{k}\\
+&=((J'_{2x}\cap H)\uplus (J^{2 \prime}_{3}\cap  J_3))\setminus \mbrc{k}\text{ since } J_3\cap J'_{2x} = \emptyset \text{ and } H\cap J^{2 \prime}_{3} = \emptyset\\
+& =((J'_{2x}\cap H)\uplus J^{2 \prime}_{3})\setminus \mbrc{k}\text{ since } J^{2 \prime}_{3}\subseteq J_3\\
+& =((J'_1\cap H)\uplus J^{1 \prime}_{3})\setminus \mbrc{k}\quad \text{ since } J^{1 \prime}_{3}=J^{2 \prime}_{3} \text{ and } J'_1 \cap H = J'_{2x} \cap H\\
+&= ((J'_1 \cap H) \uplus (J^{1 \prime}_{3} \cap J_3)) \setminus \mbrc{k}\text{ since } J^{1 \prime}_{3}\subseteq J_3\\ 
+& = (J'_1\cap (J_3 \uplus H)) \uplus ((J^{1 \prime}_{3} \cap (J_3 \uplus H)) \setminus \mbrc{k} \text{ since } J_3\cap J'_{1} = \emptyset \text{ and } H\cap J^{1 \prime}_{3} = \emptyset\\
+		& = \mpar{(J'_1  \uplus J^{1 \prime}_{3})\setminus \mbrc{k}} \cap \mpar{(J_{3} \uplus H) \setminus \mbrc{k}}\\
+		& = J'_{13} \cap H'
+\end{align*}
+
+In this case the composition gives: \[g_{13} \Leftrightarrow g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k} \text{ and }
+g_{23x}  \Leftrightarrow g_{2x} \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk}\]
+As $k \in H$ we have   
+$\beta_{1k} = \beta_{2xk}$ then we  deduce:
+\[g^1_3 \wedge \alpha^1_3=\beta_{1k}  \Leftrightarrow g^2_3 \wedge \alpha^2_3= \beta_{2xk}\]
+The proof of the rest  is based on the following facts: 
+\begin{enumerate}
+\item  Because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.
+By construction of  $t_{13}$ and $t_{23}$ we have $\alpha_{13}=
+\alpha_{1}$ and $\alpha_{23x}=\alpha_{2x}$. So we deduce: 
+$\alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$.
+\item By composition we have also: \\ $\beta_{13j}^{j\in J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
+and $\beta_{23xj}^{j\in J'_{23}}= \beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }$\\
+Therefore, we have for all $j\in J'_{13}$ (recall that $J'_{13}=J'_{23}$):  \[\beta_{13j} = \beta_{23xj} \Rightarrow (j\in J_1 \land \beta_{1j} = \beta_{2xj}) \vee (j\in J_3^1 \land \beta^1_{3j}= \beta^2_{3j})\]
+\item 
+Considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up to renaming)  we have: \\
+${\displaystyle V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}} \vdash \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$\\
+The disjunction with the following hypothesis:\\ $V_{1} \uplus V_{2} \uplus \fvars{t_1}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}}$  will give:
+\begin{align*}
+ V_{1} \uplus V_{2}  \uplus V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}}\vdash &    \bigwedge_\subbox{v_3\in V_3}\!\!
+v^1_3=v^2_3 \implies {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}} \vee {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}\\
+\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\!
+v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{2x}   \cap H)\uplus J^{2 \prime}_3 } \beta_{13j} = \beta_{23xj}} \\
+\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\!
+v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in \Rightarrow   ((J'_{2x}   \cap H)\uplus J^{2 \prime}_3)\setminus \{k\} } \beta_{13j} = \beta_{23xj}} \\
+\Rightarrow    V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\!
+v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{23x}   \cap H') } \beta_{13j} = \beta_{23xj}}
+\end{align*}
 \end{enumerate}
 
+By the extension of the valuation context mentioned above in the formula $(*)$ and by using the statements resulting from the cases (a), (b) and (c), we get:
+\begin{multline*}
+V_{13} \uplus V_{23}  \uplus \fvars{t_{13}} \vdash\\
+R\mpar{s_1, s_{2}} \wedge \mpar{g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}}\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3 %\wedge s^1_3=s^2_3
+\implies  \hspace{12em}\\
+\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in (J'_{23x} \cap H')} \beta_{13j}\! =\! \beta_{23xj}\\
+			 \nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}}  \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk} 
+%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
+\end{multline*}	
+That can be re-written as follows:
+\begin{multline*}
+V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
+R\mpar{s_1, s_{2}} \wedge g_{13}  \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3
+\implies  \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\
+			\nwedge g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}}   
+\end{multline*}
+
+Moreover, we have  for any transition $t_3$ in $A_3$ relying $s_3$ and $s^{\prime}_3$ the following:
+\begin{multline*}
+V_{13} \uplus V_{23}  \uplus \fvars{t_{13}} \vdash\\
+\bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3  \wedge s^1_3 = s^2_3 \implies \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3)  \wedge s^{1\prime}_3 = s^{2\prime}_3 
+\end{multline*}
+
+Furthermore, by hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
+\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
+Thus, we get:
+\begin{multline*}
+V_{13} \uplus V_{23} \uplus \fvars{t_1}  \cap \fvars{t_{13}} \vdash\\
+R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \reach{A_{13}}\mpar{s_{13}}
+\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
+\implies \hspace{5em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge 	g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\\
+		  \wedge \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
+\wedge \bigwedge_\subbox{v_3\in V_3}  \psi_{13}(v^1_3)=\psi_{13}(v^2_3)\wedge s^{1\prime}_3=s^{2\prime}_3
+		\end{array}}   
+\end{multline*}
+
+From the two previous formulas, we get:
+\begin{multline*}
+V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
+R\mpar{s_1, s_{2}} \wedge g_{13} \land \reach{A_{13}}\mpar{s_{13}} \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3 \wedge s^1_3 = s^2_3
+\implies \hspace{7em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\land  \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}		\\
+			  R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge
+ \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3) \wedge s^{1\prime}_3 = s^{2\prime}_3
+		\end{array}}   
+\end{multline*}
+
+Because of the independence of the substitution domains, we simplify and get the expected formula:
+	\begin{multline*}
+  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ R^{\prime}\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
+			\nwedge g_{23x} \wedge R^{\prime}\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
+		\end{array}} 
+	\end{multline*}
+
+\smallskip
+
+\paragraph{Second case: Only the encompassing automaton performs a transition}
+ $t_{13}$ is obtained  by  the transition $t_1=\OTx{1}{}{1}{1}$ alone with the state $s^1_3$ unchanged, if $k \not\in J_1'$
+\[t_{13} = \OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, s^1_3}}{\alpha_1}{\beta_{1j}^{j \in J'_1}}{g_1}{\psi_1}
+\]
+We then obtain a family of OTs by the simulation of $A_1$ by $A_2$ (stated above).
+As  $k \in H$ we have $k \not\in J'_{2x}$ and we build:
+\[t_{23x} = \left(
+\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, s^2_3}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x}}}{g_{2x}}{\psi_{2x}} \right)^{x\in X}\]
+
+These two cases define (depending on how $t_{13}$ is built) the family $t_{23x}$ of OTs we are looking for.
+Thus, for both cases we have to prove the following:
+\begin{align*}		
+		&\mpar{\forall x \in X, J'_{23x} \cap H' =
+ J'_{13} \cap H'} \text{ and }\\
+		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ & R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
+			\nwedge g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
+		\end{array}} 
+	\end{align*}
+
+Recall in this case $k \notin J'_1$, $\forall x \in X$ we have
+\begin{align*}		
+J'_{23x} \cap H' & = J'_{2x}  \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
+& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
+& = \mpar{J'_1\cap H } \text{ since } J'_1 \cap H = J'_{2x} \cap H\\
+& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'
+\end{align*}
+
+The proof of the rest of the formula follows the same steps as the previous case the only argument that changes is that by composition we obtain:  $g_{13} \Leftrightarrow g_1$ and
+$g_{23x}  \Leftrightarrow g_{2x}$.\\
+
+\item  Lastly, we have to prove the satisfaction of the deadlock reduction condition, i.e., for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
+\begin{multline*}
+V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_{23}} \vdash \\ \left(R^{\prime}\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_1 \in \fOT{s_{13}}} \fguard{t_{13}} \right)
+\end{multline*}
+Let's start  with the hypothesis of the theorem stating that $\wrel{A_1}{A_2}{H}$, thus we have for all  $\mpar{s_1, s_2} \in S_1 \times S_2$ 
+\begin{multline*}
+V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
+\end{multline*}
+We have a second hypothesis stating that the result of the composition \(A_1\subst{A_3}{k}\) is non-blocking, which leads to:
+\begin{multline*}
+V_{13}  \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \left( \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \right)
+\end{multline*}
+We use the the first, we extend the valuation to cover the variables of  $t^2_3$ in $t_{23}$ using their value in $t_3$ and because $\fvars{t_{13}} \vdash \reach{A_{13}}\mpar{s_{13}}$, we get:
+\begin{multline*}
+V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}  \wedge \reach{A_{13}}\mpar{s_{13}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}   \wedge \reach{A_{13}}\mpar{s_{13}}\right)
+\end{multline*}
+By transitivity with the second hypothesis we obtain:
+\begin{multline*}
+V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}   \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}\right)
+\end{multline*}
+That implies:
+\begin{multline*}
+V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(\underbrace{R\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3}_{R^{\prime}(s_{13},s_{23})}  \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}   \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}\right)
+\end{multline*}
+which gives us what we needed to demonstrate. \qed
+
 \end{enumerate}
+
 %\section{a recuperer si on se rend compte que c'est utile}

### 2023-01-26 2021-Refinement/paper/refinementarticleV2.tex
TODOs

@@
 
-Recall in this case $k \notin J'_1$, $\forall x \in X$ we have
+Recall in this case \LUDO{ WHICH CASE???}  $k \notin J'_1$, $\forall x \in X$ we have
 \begin{align*}		
@@
 
-\item  Lastly, we have to prove the satisfaction of the deadlock reduction condition, i.e., for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
+\item \LUDO{ OLD OUTDATED PROOF?????} Lastly, we have to prove the satisfaction of the deadlock reduction condition, i.e., for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
 \begin{multline*}
@@
 \end{multline*}
-which gives us what we needed to demonstrate. \qed
+which gives us what we needed to demonstrate.} \qed
 

### 2023-02-16 2021-Refinement/paper/refinementarticleV2.tex
petits improvments

--- 2023-01-09 2021-Refinement/paper/refinementarticleV2.tex
@@
 \usepackage{macrospNets}
-
+\usepackage{cancel}
 \AtBeginDocument{\renewcommand\setminus{\smallsetminus}}
@@
 
-Recall in this case $k \notin J'_1$, $\forall x \in X$ we have
+Recall in this second case (where only the encompassing automaton performs a transition $t_{13}$)  $k \notin J'_1$, $\forall x \in X$ we have
 \begin{align*}		
@@
 
-\item  Lastly, we have to prove the satisfaction of the deadlock reduction condition, i.e., for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
-\begin{multline*}
-V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_{23}} \vdash \\ \left(R^{\prime}\mpar{s_{13}, s_{23}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} \implies \bigvee_\subbox{t_1 \in \fOT{s_{13}}} \fguard{t_{13}} \right)
-\end{multline*}
+\item \RAB{Part in progress} Lastly, we have to prove the satisfaction of the deadlock reduction condition, i.e., for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
+\begin{multline*}
+V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_{23}} \vdash \\ R\mpar{s_{13}, s_{23}}  \implies \bigvee_\subbox{t_1 \in \fOT{s_{13}}} \fguard{t_{13}} \vee \neg \mpar{\,\,\,\,\, \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} }
+\end{multline*}
+
 Let's start  with the hypothesis of the theorem stating that $\wrel{A_1}{A_2}{H}$, thus we have for all  $\mpar{s_1, s_2} \in S_1 \times S_2$ 
 \begin{multline*}
-V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
-\end{multline*}
-We have a second hypothesis stating that the result of the composition \(A_1\subst{A_3}{k}\) is non-blocking, which leads to:
-\begin{multline*}
-V_{13}  \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \left( \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \right)
+V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2}  \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \vee \neg\mpar{\,\,\,\,\,\bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}}
+\end{multline*}
+
+\RAB{ Il faudra exprimer une condition de non blocage peut on exprimer comme ceci}
+the result of the composition \(A_1\subst{A_3}{k}\) is non-blocking:
+\begin{multline*}
+V_{13}  \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \left( \cancel{\reach{A_{13}}\mpar{s_{13}} \wedge} \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \right)
 \end{multline*}

### 2023-02-16 2021-Refinement/paper/refinementarticleV2.tex
point 3

@@
 \begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in (J'_{23x} \cap H')} \beta_{13j}\! =\! \beta_{23xj}\\
-			 \nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in (J'_{23x} \cap H')} \beta_{13j}\! =\! \beta_{23xj}\nwedge\\
+			  g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
 		\end{array}}  \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk} 
@@
 \begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\
-			\nwedge g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge\\
+			g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
 		\end{array}}   
@@
 \begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\land  \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}		\\
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\land  \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}		\nwedge\\
 			  R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge
@@
   V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ R^{\prime}\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
-			\nwedge g_{23x} \wedge R^{\prime}\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge\\[12pt]
+			 g_{23x} \wedge R^{\prime}\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
 		\end{array}} 
@@
 		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ & R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
-			\nwedge g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge\\[12pt]
+			g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
 		\end{array}} 
@@
 
-Recall in this second case (where only the encompassing automaton performs a transition $t_{13}$)  $k \notin J'_1$, $\forall x \in X$ we have
+Recall in this second case, i.e. where only $A_1$ performs a transition $t_{13}$,  $k \notin J'_1$, $\forall x \in X$ we have
 \begin{align*}		
@@
 \begin{multline*}
-V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_{23}} \vdash \\ R\mpar{s_{13}, s_{23}}  \implies \bigvee_\subbox{t_1 \in \fOT{s_{13}}} \fguard{t_{13}} \vee \neg \mpar{\,\,\,\,\, \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}} }
+V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_{23}} \vdash \\ R\mpar{s_{13}, s_{23}} \nwedge  \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}) \implies   \neg (\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
 \end{multline*}
@@
 \begin{multline*}
-V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2}  \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \vee \neg\mpar{\,\,\,\,\,\bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}}
-\end{multline*}
-
-\RAB{ Il faudra exprimer une condition de non blocage peut on exprimer comme ceci}
-the result of the composition \(A_1\subst{A_3}{k}\) is non-blocking:
-\begin{multline*}
-V_{13}  \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash \left( \cancel{\reach{A_{13}}\mpar{s_{13}} \wedge} \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}} \right)
-\end{multline*}
-We use the the first, we extend the valuation to cover the variables of  $t^2_3$ in $t_{23}$ using their value in $t_3$ and because $\fvars{t_{13}} \vdash \reach{A_{13}}\mpar{s_{13}}$, we get:
-\begin{multline*}
-V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}  \wedge \reach{A_{13}}\mpar{s_{13}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}   \wedge \reach{A_{13}}\mpar{s_{13}}\right)
-\end{multline*}
-By transitivity with the second hypothesis we obtain:
-\begin{multline*}
-V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(R\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}   \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}\right)
-\end{multline*}
-That implies:
-\begin{multline*}
-V_1 \uplus V_2 \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \left(\underbrace{R\mpar{s_1, s_2} \wedge \reach{A_{13}}\mpar{s_{13}} \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3}_{R^{\prime}(s_{13},s_{23})}  \wedge \bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}   \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}\right)
+V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \nwedge \neg (\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}) \implies   \neg(\bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2})
+\end{multline*}
+Because the guards from transitions of $A_1$ are still transitions of $A_{13}$, we get:  
+\begin{multline*}
+V_{13}  \uplus \biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}} \vdash \neg(\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}) \implies \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})
+\end{multline*}
+
+Similarly, transitions of $A_2$ are still transitions of $A_{23}$,  we get:
+\begin{multline*}
+V_{23}  \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash \neg(\bigvee_\subbox{t_1 \in \fOT{s_2}} \fguard{t_2}) \implies \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
+\end{multline*}
+From these three formulas we deduce:
+  \begin{multline*}
+V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ R\mpar{s_1, s_2} \nwedge \neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}) \implies   \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
+\end{multline*}
+
+which also implies:
+\begin{multline*}
+V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \underbrace{R\mpar{s_1, s_2} \wedge  \mpar{\,\,\bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3 \wedge s^1_3=s^2_3}}_{R^{\prime}(s_{13},s_{23})}  \wedge \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})   \implies \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
 \end{multline*}

### 2023-02-17 2021-Refinement/paper/refinementarticleV2.tex
Theorem 3

@@
 
-\TODO{Je reintroduis la notion de reachability et non introduction de blocage}
+\TODO{La section 4.1 reintroduit la notion de reachability et non introduction de blocage}
 \subsection{Deadlock Reduction, Reachability, and Composition}
@@
 
-\TODO{Fin reintrod.}
+\TODO{Fin reintroduction}
 
@@
  refinement is compositional in the sense that it is sufficient to prove refinement for the composed automata separately to obtain a refinement relation.
-The second part, i.e. proving that placing in the same context two open automata in refinement, we obtain two open automata in refinement is left for future works.
+The second part,  proving that placing in the same context two open automata in refinement, we obtain two open automata in refinement is left for future works.
 %
@@
 Let $A_1$, $A_2$ and $A_3$ be three open automata with $\wrel{A_1}{A_2}{H}$. 
-Let $J_3$ be the set of holes of $A_3$.
+Let $J_3$ be the set of holes of $A_3$ and suppose that $k \in H$.
 %Suppose that \(k \in H\) and that \(A_1\subst{A_3}{k}\) is non-blocking.
@@
 \end{theorem}
-
-Pictorially, the theorem has the following form:
+\RAB{A t-on des conditions sur H?}
+
+Pictorially, the theorem states the following result:
 
@@
 If the hole $k$ is involved the considered relation  implies that valuations in $A_3$ are equal (i.e., the value for each variable are the same in both valuations), after a transition we should obtain ``equal'' valuations because post-conditions are deterministic.
-\begin{example} The composition of the refined \texttt{database} and the \texttt{counter} is again an open automata, depicted in Fig.~\ref{Fig:ComposeRefine}.
+
+\begin{theorem}[Congruence]
+Let $A_1$, $A_2$ and $A_3$ be three open automata with $\wrel{A_2}{A_3}{H}$. 
+ $\wrel{A_1}{A_2}{H}$.  Let $J_3$ be the set of holes of $A_3$ and suppose that \(k \in H\).
+We have: \[\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{J_1 \uplus H \setminus \mbrc{k}}\]
+\end{theorem}
+
+\begin{example} \RAB{cet exemple illustre plutot  que la composition est un raffinement, i.e.,  $\wrel{A_1\subst{A_2}{k}}{A_1}{J_1   \setminus \mbrc{k}}$ doit-on ajouter ce resultat comme un lemme?}
+
+The composition of the refined \texttt{database} and the \texttt{counter} is again an open automata, depicted in Fig.~\ref{Fig:ComposeRefine}.
 As stated by the theorem,  it can easily be verified that this automaton is a refinement of the automaton of the figure Fig.~\ref{Def:CompOA}, i.e.
@@
 \begin{quote}
-Suppose that $\wrel{A_1}{A_2}{H}$, \(k \in H\) and that \(A_1\subst{A_3}{k}\) is non-blocking. We have: 
+Suppose that $\wrel{A_1}{A_2}{H}$, \(k \in H\) \cancel{and that \(A_1\subst{A_3}{k}\) is non-blocking}. We have: 
 \[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{J_3 \uplus H \setminus \mbrc{k}}\]
@@
 
-Furthermore, by hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
+\RAB{ I think there is no need to the no blocking condition} Furthermore, by hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
 \[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
@@
 			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge 	g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\\
-		  \wedge \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
-\wedge \bigwedge_\subbox{v_3\in V_3}  \psi_{13}(v^1_3)=\psi_{13}(v^2_3)\wedge s^{1\prime}_3=s^{2\prime}_3
+		  \wedge \cancel{\reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
+\wedge} \bigwedge_\subbox{v_3\in V_3}  \psi_{13}(v^1_3)=\psi_{13}(v^2_3)\wedge s^{1\prime}_3=s^{2\prime}_3
 		\end{array}}   
@@
 V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
-R\mpar{s_1, s_{2}} \wedge g_{13} \land \reach{A_{13}}\mpar{s_{13}} \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3 \wedge s^1_3 = s^2_3
+R\mpar{s_1, s_{2}} \wedge g_{13} \land \cancel{\reach{A_{13}}\mpar{s_{13}} \land} \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3 \wedge s^1_3 = s^2_3
 \implies \hspace{7em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
@@
 
-\paragraph{Second case: Only the encompassing automaton performs a transition}
+\paragraph{Second case: Only the encompassing automaton performs a transition.}
  $t_{13}$ is obtained  by  the transition $t_1=\OTx{1}{}{1}{1}$ alone with the state $s^1_3$ unchanged, if $k \not\in J_1'$
@@
 
-\item \RAB{Part in progress} Lastly, we have to prove the satisfaction of the deadlock reduction condition, i.e., for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
+\item \TODO{To check this point:} Lastly, we have to prove the satisfaction of the deadlock reduction condition, i.e., for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
 \begin{multline*}
@@
 \end{multline*}
-From these three formulas we deduce:
+From the three previous formulas we deduce:
   \begin{multline*}
@@
 
+\section{Proof of Congruence}
+Suppose $\wrel{A_2}{A_3}{H}$ and  $k \in H$. We have: \[\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{J_1 \uplus H \setminus \mbrc{k}}\]
+\proof
+Let us denote by $A_{12}$ (resp.
+$A_{13}$) the open automaton resulting from $A_1\subst{A_2}{k}$ (resp.
+$A_1\subst{A_3}{k}$),  to prove the theorem it is sufficient to prove that there exists a relation between states of the two open automata that satisfies the conditions of the Definition \ref{Def:OA-Refinement}.
+
+We denote $A_1=  \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}$ and \(A_2 = \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and $A_3 = \OA{S_3}{s_{03}}{J_3}{V_3}{\sigma_{03}}{T_3}$.
+
+% The proof requires  to rename the variables of one instance of the two $A_3$ automata to avoid clashes in variable names (this is required by the definition of refinement).
+In practice we will use superscripts ${}^1$ and ${}^2$ to distinguish elements of the two instances of $A_3$.
+
+Let $R$ be the refinement relation relating states of $A_2$ and $A_3$. 
+Let us denote with $t^2$ and $t^3$  the elements of $A_2$ and $A_3$ respectively.
+Consider any two states $s_{12} = \mpar{s_1,s^1_2}$ and $s_{13} = \mpar{s^2_1,s_3}$ ($s^1_1$ and $s^2_1$  are the same with renaming).
+We define a relation $R'$ relating states of $s_{12}$ and $s_{13}$ as follows:
+\[ R' \mpar{s_{12}, s_{13}} = R\mpar{s_{2}, s_{2}} \wedge \bigwedge_\subbox{v_1\in V_1}
+ v^1_1=v^2_1\wedge s^1_1 = s^2_1\]
+Let us denote $H'=H\cup J_1 \setminus\{k\}$.
+We want to prove that $\mpar{R', H'}$  is a hole-tracking simulation of $A_{12}$ and $A_{13}$. As for the previous proof we deal with cases:
+\begin{enumerate}
+\item \TODO{Pareil que le theorem precedent}
+
+\item Second, we need to prove for any OT $t_{12}$ in $T_{12}$ originating from $s_{12}$
+
+\begin{align*}
+		&  \OTx{12}{}{12}{12} \in \fOT{s_{12}}
+\end{align*}		
+there exists an indexed family $t_{13x}$ of OTs originating from $s_{13}$ that simulates it: 
+\begin{align*}
+		&  \mpar{\OTx{13}{x}{13x}{13x} \in \fOT{s_{13}}}^{x \in X}
+\end{align*}	
+such that  $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$ and
+\begin{multline*}	
+V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \wedge\\[12pt]
+			 g_{13x} \wedge R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
+		\end{array}} 
+	\end{multline*}
+By definition of composition and open automata refinement we have: 
+\begin{align*}
+&V_{12}= V^1_1\uplus V_3 \text{ and }
+V_{13}= V^2_1\uplus V_3\\
+& H'=H_{23}\uplus J_1 \setminus \{k\} \subseteq J_1\uplus \mpar{J_2 \cap J_3} \setminus \{k\} = \mpar{J^1_1\uplus J_2 \setminus \{k\} } \cap \mpar{J^2_1\uplus J_3 \setminus \{k\}} = J_{12 } \cap J_{13} \\
+\end{align*}
+We have by hypothesis $\wrel{A_2}{A_3}{H}$, then for any open transition $t_2$ in $T_2$  originating from $s_2$:
+\begin{align*}
+\OTx{2}{}{2}{2} \in \fOT{s_2}
+\end{align*}
+there exists an indexed family of OTs originating from $s_{2}$: 
+\begin{align*}
+\mpar{\OTx{3}{x}{3x}{3x} \in \fOT{s_{3}}}^{x \in X} 
+\end{align*}
+such that $\forall x \in X, J'_{3x} \cap H = J'_2 \cap H$ and
+\begin{multline*}
+%\everymath{\displaystyle}
+V_2 \uplus V_3 \uplus \fvars{t_2} \vdash\\ R\mpar{s_2, s_3} \wedge g_2 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_2 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj} \nwedge\\
+			 g_{3x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
+		\end{array}}  \qquad \quad (*)
+\end{multline*}	
+\smallskip
+
+Consider any transition $t_{12}$ in $A_{12}$. Based on the definition of the composition  $t_{12}$ can be obtained from two different cases,  we will consider the two cases
+separately.
+
+\paragraph{First case: Both automata perform a transition.} The transition $t_{12}$  is obtained by the composition of transition $t_2=\OTx{2}{}{2}{2}$ and a transition \[t_1^1=
+\OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{   {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1} \qquad \text{ when } k \in {J^1_{1}}^{\prime}
+\] The result:
+%%%% Attention deactiver ici
+\[
+t_{12} = \OT{\mpar{s^1_1, s_2}}{\mpar{{s^1_1}',s'_2 }}{\alpha^1_1}{{\beta^1_{1j}}^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {(\beta_{2j})^{j \in J^{\prime}_2} }}{g^1_1 \wedge g_2 \wedge \alpha_2 = \beta^1_{1k}}{\psi^1_1 \uplus \psi_2} \qquad \text{ where } k \in {J^1_{1}}^{\prime}
+\]
+
+We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (as stated above).
+By hypothesis we have $k \in H$, so in the case where $k \in {J^1_{1}}^{\prime}$, we deduce that $k \in J'_{3x}$ we can  then build  a family of OTs $t_{13x}^{x\in X}$ with the same transitions of $A_1$ (up to renaming) as those used to build $t_{12}$.
+\[
+t_{13x} = \left(\OT{\mpar{s^2_1, s_3}}{\mpar{{s^2_{1}}',s'_{3x}}}{\alpha^2_{1}}  {{(\beta^2_{1j})^{j \in J^{2 \prime}_1}}\uplus \beta_{3xj}^{j \in J'_{3x}  \setminus \{k\}} }{g_{3x} \wedge g^2_1 \wedge \alpha^2_1 = \beta_{3xk}}{\psi_{3x} \uplus \psi^2_1}
+\right)^{x\in X}\]
+Recall that in this case  $k \in {J^1_{1}}^{\prime}$, so $\forall x \in X$ we have
+\begin{align*}
+  J'_{31x} \cap H'  
+&=((J'_{3x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{1} ) \cap (H\uplus J_1 \setminus\{k\} )\\
+&=((J'_{3x}\cap (H\uplus J_1))\uplus (J^{2 \prime}_{1}\cap (H\uplus J_1)))\setminus \mbrc{k}\\
+&=((J'_{3x}\cap H)\uplus (J^{2 \prime}_{1}\cap  J_1))\setminus \mbrc{k}\text{ since } J_1\cap J'_{3x} = \emptyset \text{ and } H\cap J^{2 \prime}_{1} = \emptyset\\
+& =((J'_{3x}\cap H)\uplus J^{2 \prime}_{1})\setminus \mbrc{k}\text{ since } J^{2 \prime}_{1}\subseteq J_1\\
+& =((J'_2\cap H)\uplus J^{1 \prime}_{1})\setminus \mbrc{k} \text{ since } J^{1 \prime}_{1}=J^{2 \prime}_{1} \text{ and } J'_2 \cap H = J'_{3x} \cap H\\
+&= ((J'_2 \cap H) \uplus (J^{1 \prime}_{1} \cap J_1)) \setminus \mbrc{k}\text{ since } J^{1 \prime}_{1}\subseteq J_1\\ 
+& = (J'_2\cap (J_1 \uplus H)) \uplus ((J^{1 \prime}_{1} \cap (J_1 \uplus H)) \setminus \mbrc{k} \text{ since } J_1\cap J'_{2} = \emptyset \text{ and } H\cap J^{1 \prime}_{1} = \emptyset\\
+		& = \mpar{(J'_2  \uplus J^{1 \prime}_{1})\setminus \mbrc{k}} \cap \mpar{(J_{1} \uplus H) \setminus \mbrc{k}}\\
+		& = J'_{12} \cap H'
+\end{align*}
+
+=============================
+\paragraph{Second case: Only the encompassing automaton performs a transition.}
+* or by an the transition $t_1^2=
+\OT{ s^2_1}{{s^2_1}'}{\alpha_1^2}{{(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{ g^2_1 }{ \psi^2_1}$  alone with the state $s_2$ unchanged, if $k \not\in {J^1_{1}}^{\prime}$
+\[t_{12} = \OT{\mpar{s^2_1, s_2}}{\mpar{{s^2_1}', s'_2}}{\alpha_1^2}{ {(\beta^2_{1j})^{j \in J^{1 \prime}_1} }}{g^2_1}{\psi^2_1}
+\]
+We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (stated above).
+As  $k \in H$ we have $k \not\in J'_{2x}$ and we build:
+\[t_{13x} = \left(
+\OT{\mpar{s^1_1, s_3}}{\mpar{s^2_1,s'_{2x}}}{\alpha_{3x}}{\beta_{3xj}^{j \in J'_{3x}}}{g_{3x}}{\psi_{3x}} \right)^{x\in X}\]
+
+~\qed
+\end{enumerate}
+
 %\section{Proof of Transitivity for Refinement}\label{sec:proof-transitivity}

### 2023-02-21 2021-Refinement/paper/refinementarticleV2.tex
Theorem 3
Congruence in progress

@@
 \begin{enumerate}
-\item  Because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transition $t_3$.
-By construction of  $t_{13}$ and $t_{23}$ we have $\alpha_{13}=
+\item  Because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transitions $t_3$ and .
+By construction of  $t_{13}$ and $t_{23x}$ we have $\alpha_{13}=
 \alpha_{1}$ and $\alpha_{23x}=\alpha_{2x}$. So we deduce: 
@@
 and $\beta_{23xj}^{j\in J'_{23}}= \beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }$\\
-Therefore, we have for all $j\in J'_{13}$ (recall that $J'_{13}=J'_{23}$):  \[\beta_{13j} = \beta_{23xj} \Rightarrow (j\in J_1 \land \beta_{1j} = \beta_{2xj}) \vee (j\in J_3^1 \land \beta^1_{3j}= \beta^2_{3j})\]
+Therefore, we have for all $j\in J'_{13}$ (recall that $J'_{13}=J'_{23}$):  \[\beta_{13j} = \beta_{23xj} \Rightarrow (j\in J'_1 \land \beta_{1j} = \beta_{2xj}) \vee (j\in J_3^{1\prime} \land \beta^1_{3j}= \beta^2_{3j})\]
 \item 
@@
 \Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\!
-v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in \Rightarrow   ((J'_{2x}   \cap H)\uplus J^{2 \prime}_3)\setminus \{k\} } \beta_{13j} = \beta_{23xj}} \\
+v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in    ((J'_{2x}   \cap H)\uplus J^{2 \prime}_3)\setminus \{k\} } \beta_{13j} = \beta_{23xj}} \\
 \Rightarrow    V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\!
@@
 V_{13} \uplus V_{23} \uplus \fvars{t_1}  \cap \fvars{t_{13}} \vdash\\
-R\mpar{s_1, s_{2}} \wedge g_{13}  \wedge \reach{A_{13}}\mpar{s_{13}}
+R\mpar{s_1, s_{2}} \wedge g_{13}  \cancel{\wedge \reach{A_{13}}\mpar{s_{13}}}
 \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
@@
 \begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\land  \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}		\nwedge\\
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\land  \cancel{\reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}}		\nwedge\\
 			  R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge
@@
 
-\item \TODO{To check this point:} Lastly, we have to prove the satisfaction of the deadlock reduction condition, i.e., for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
-\begin{multline*}
-V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23}\in \fOT{s_{23}}} \fvars{t_{23}} \vdash \\ R\mpar{s_{13}, s_{23}} \nwedge  \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}) \implies   \neg (\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
+\item \TODO{To check from this point:} Lastly, we have to prove the satisfaction of the deadlock reduction condition, i.e., for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
+\begin{multline*}
+V_{13} \uplus V_{23}  \vdash  R\mpar{s_{13}, s_{23}} \nwedge  \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}) \implies   \neg (\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}) 
 \end{multline*}
@@
 \begin{multline*}
-V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \nwedge \neg (\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}) \implies   \neg(\bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2})
+V_1 \uplus V_2 \vdash R\mpar{s_1, s_2} \nwedge \neg (\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}) \implies   \neg(\bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2})
 \end{multline*}
@@
 \begin{multline*}
-V_{13}  \uplus \biguplus_\subbox{t_{13} \in \fOT{s_{13}}} \fvars{t_{13}} \vdash \neg(\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}) \implies \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})
+V_{13}   \vdash \neg(\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}) \implies \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})
 \end{multline*}
@@
 \begin{multline*}
-V_{23}  \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash \neg(\bigvee_\subbox{t_1 \in \fOT{s_2}} \fguard{t_2}) \implies \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
+V_{23}   \vdash \neg(\bigvee_\subbox{t_1 \in \fOT{s_2}} \fguard{t_2}) \implies \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
 \end{multline*}
@@
   \begin{multline*}
-V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ R\mpar{s_1, s_2} \nwedge \neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}) \implies   \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
+V_{13} \uplus V_{23} \vdash R\mpar{s_1, s_2} \nwedge \neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}) \implies   \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
 \end{multline*}
@@
 \begin{multline*}
-V_{13} \uplus V_{23} \uplus \biguplus_\subbox{t_{23} \in \fOT{s_{23}}} \fvars{t_{23}} \vdash\\ \underbrace{R\mpar{s_1, s_2} \wedge  \mpar{\,\,\bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3 \wedge s^1_3=s^2_3}}_{R^{\prime}(s_{13},s_{23})}  \wedge \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})   \implies \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
+V_{13} \uplus V_{23}  \vdash \\ \underbrace{R\mpar{s_1, s_2} \wedge  \mpar{\,\,\bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3 \wedge s^1_3=s^2_3}}_{R^{\prime}(s_{13},s_{23})}  \wedge \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})   \implies \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
 \end{multline*}
@@
 V_{13}= V^2_1\uplus V_3\\
-& H'=H_{23}\uplus J_1 \setminus \{k\} \subseteq J_1\uplus \mpar{J_2 \cap J_3} \setminus \{k\} = \mpar{J^1_1\uplus J_2 \setminus \{k\} } \cap \mpar{J^2_1\uplus J_3 \setminus \{k\}} = J_{12 } \cap J_{13} \\
+& H'=H_{23}\uplus J_1 \setminus \{k\} \subseteq J_1\uplus \mpar{J_2 \cap J_3} \setminus \{k\} = \mpar{J^1_1\uplus J_2 \setminus \{k\} } \cap \mpar{J^2_1\uplus J_3 \setminus \{k\}} = J_{12 } \cap J_{13}
 \end{align*}
@@
 \[
-t_{12} = \OT{\mpar{s^1_1, s_2}}{\mpar{{s^1_1}',s'_2 }}{\alpha^1_1}{{\beta^1_{1j}}^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {(\beta_{2j})^{j \in J^{\prime}_2} }}{g^1_1 \wedge g_2 \wedge \alpha_2 = \beta^1_{1k}}{\psi^1_1 \uplus \psi_2} \qquad \text{ where } k \in {J^1_{1}}^{\prime}
+t_{12} = \OT{\mpar{s^1_1, s_2}}{\mpar{{s^1_1}',s'_2 }}{\alpha^1_1}{{\beta^1_{1j}}^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {(\beta_{2j})^{j \in J^{\prime}_2} }}{g^1_1 \wedge g_2 \wedge \alpha^1_1 = \beta_{2k}}{\psi^1_1 \uplus \psi_2} \qquad \text{ where } k \in {J^1_{1}}^{\prime}
 \]
@@
 \right)^{x\in X}\]
-Recall that in this case  $k \in {J^1_{1}}^{\prime}$, so $\forall x \in X$ we have
+Recall that in this case  $k \in {J^1_{1}}^{\prime}$, so $\forall x \in X$ we have:
 \begin{align*}
@@
 
-=============================
+In this case the composition gives: \[g_{12} \Leftrightarrow g^1_1 \wedge g_2 \wedge \alpha^1_1=\beta_{2k} \text{ and }
+g_{13x}  \Leftrightarrow g^2_1 \wedge g_{3x} \wedge  \alpha^2_1=\beta_{3xk}\]
+As $k \in H$ we have   
+$\alpha^1_1= \alpha^2_1$ then we  deduce:
+\[g^1_1 \wedge \alpha^1_1=\beta_{2k}  \Leftrightarrow g^2_1 \wedge \alpha^2_1= \beta_{3xk}\]
+
+The proof of the rest  is based on the following facts: 
+\begin{enumerate}
+\item  Because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transitions $t_2$ and $t_{3x}$.
+By construction of  $t_{12}$ and $t_{13x}$ we have $\alpha_{12}=
+\alpha^1_{1}$ and $\alpha_{13x}=\alpha^2_{1}$. Since  $\alpha^1_{1}$ and  $\alpha^2_{1}$ are the same (up the renaming. So we deduce: 
+$\alpha_{12} = \alpha_{13x}$.
+\item By composition we have also: \\ $\beta_{12j}^{j\in J'_{12}}= (\beta^1_{1j})^{j \in J^{1 \prime}_{1} \setminus \{k\}} \uplus   (\beta_{2j})^{j \in J'_{2} }$
+and $\beta_{13xj}^{j\in J'_{13}}= (\beta^2_{1j})^{j \in J^{2 \prime}_{1}  \setminus \{k\}}  \uplus \beta_{3xj}^{j \in J'_{3x}  \setminus \{k\}}$\\
+Therefore, we have for all $j\in J'_{12}$ (recall that $J'_{12}=J'_{13}$):  \[\beta_{12j} = \beta_{13xj} \Rightarrow (j\in J^{1\prime}_1 \land \beta^1_{1j} = \beta^2_{1j}) \vee (j\in J'_2 \land \beta_{2j}= \beta_{3xj})\]
+\item 
+Considering $\beta^1_{1j}$ and  $\beta^2_{1j}$  are the same (up to renaming)  we have: \\
+${\displaystyle V^1_{1} \uplus V^2_{1} \uplus \fvars{t_{12}} \vdash \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1\implies \bigwedge_\subbox{j \in J^{2 \prime}_1} \beta^1_{1j}= \beta^2_{1j}}$\\
+The disjunction with the following hypothesis:\\ $V_{2} \uplus V_{3} \uplus \fvars{t_2}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj}}$  will give:
+\begin{align*}
+ V_{2} \uplus V_{3}  \uplus V^1_{1} \uplus V^2_{1} \uplus \fvars{t_{12}}\vdash &    \bigwedge_\subbox{v_1\in V_1}\!\!
+v^1_1=v^2_1 \implies {\displaystyle \bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj}} \vee {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_1} \beta^1_{1j}= \beta^2_{1j}}\\
+\Rightarrow  V_{12} \uplus V_{13}  \uplus \fvars{t_{12}}\vdash & \bigwedge_\subbox{v_1\in V_1}\!\!
+v^1_1=v^2_1\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{3x}   \cap H)\uplus J^{2 \prime}_1 } \beta_{12j} = \beta_{13xj}} \\
+\Rightarrow  V_{12} \uplus V_{13}  \uplus \fvars{t_{12}}\vdash & \bigwedge_\subbox{v_1\in V_1}\!\!
+v^1_1=v^2_1\implies {\displaystyle \bigwedge_\subbox{j \in    ((J'_{3x}   \cap H)\uplus J^{2 \prime}_1)\setminus \{k\} } \beta_{12j} = \beta_{13xj}} \\
+\Rightarrow    V_{12} \uplus V_{12}  \uplus \fvars{t_{12}}\vdash & \bigwedge_\subbox{v_1\in V_1}\!\!
+v^1_1=v^2_1\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{13x}   \cap H') } \beta_{12j} = \beta_{13xj}}
+\end{align*}
+\end{enumerate}
+
+By the extension of the valuation context mentioned above in the formula $(*)$ and by using the statements resulting from the cases (a), (b) and (c), we get:
+\begin{multline*}
+V_{13} \uplus V_{23}  \uplus \fvars{t_{13}} \vdash\\
+R\mpar{s_2, s_{3}} \wedge \mpar{g_2 \wedge g^1_1 \wedge \alpha^1_1=\beta_{2k}}\wedge \bigwedge_\subbox{v_1\in V_1}  v^1_1=v^2_1 %\wedge s^1_1=s^2_1
+\implies  \hspace{12em}\\
+\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in (J'_{13x} \cap H')} \beta_{12j}\! =\! \beta_{13xj}\nwedge\\
+			  g_{3x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
+		\end{array}}  \wedge g^2_1 \wedge \alpha^2_1=\beta_{3xk} 
+%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
+\end{multline*}	
+That can be re-written as follows:
+\begin{multline*}
+V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
+R\mpar{s_2, s_{3}} \wedge g_{12}  \land \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1
+\implies  \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge\\
+			g_{13x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
+		\end{array}}   
+\end{multline*}
+
+Moreover, we have  for any transition $t_1 $ in $A_1$ relying $s_3$ and $s^{\prime}_1$ the following:
+\begin{multline*}
+V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash\\
+\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1  \wedge s^1_1 = s^2_1 \implies \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{12}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1 
+\end{multline*}
+
+From the two previous formula, we get:
+\begin{multline*}
+V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash\\
+R\mpar{s_2, s_{3}} \wedge g_{12}  \land \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1  \wedge s^1_1 = s^2_1 
+\implies \hspace{12em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge g_{13x} \wedge \\
+			 R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}} \wedge \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{12}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1
+		\end{array}}   
+\end{multline*}
+
+Because of the independence of the substitution domains, we simplify and get the expected formula:
+\begin{multline*}
+V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash
+R\mpar{s_{12}, s_{13}} \wedge g_{12} 
+\implies \hspace{10em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge g_{13x} \wedge 
+			 R\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
+		\end{array}}   
+\end{multline*}
+
 \paragraph{Second case: Only the encompassing automaton performs a transition.}
-* or by an the transition $t_1^2=
-\OT{ s^2_1}{{s^2_1}'}{\alpha_1^2}{{(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{ g^2_1 }{ \psi^2_1}$  alone with the state $s_2$ unchanged, if $k \not\in {J^1_{1}}^{\prime}$
-\[t_{12} = \OT{\mpar{s^2_1, s_2}}{\mpar{{s^2_1}', s'_2}}{\alpha_1^2}{ {(\beta^2_{1j})^{j \in J^{1 \prime}_1} }}{g^2_1}{\psi^2_1}
+  $t_{12}$ is obtained by the transition
+$\OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{{(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1}$  alone with the state $s_2$ unchanged, if $k \not\in {J^1_{1}}^{\prime}$
+\[t_{12} = \OT{\mpar{s^1_1, s_2}}{\mpar{{s^1_1}', s_2}}{\alpha_1^1}{ {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{g^1_1}{\psi^1_1}
 \]
 We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (stated above).
-As  $k \in H$ we have $k \not\in J'_{2x}$ and we build:
+As  $k \in H$ we have $k \not\in J^{1\prime}_1$ and we build:
 \[t_{13x} = \left(
-\OT{\mpar{s^1_1, s_3}}{\mpar{s^2_1,s'_{2x}}}{\alpha_{3x}}{\beta_{3xj}^{j \in J'_{3x}}}{g_{3x}}{\psi_{3x}} \right)^{x\in X}\]
-
+\OT{\mpar{s^2_1, s_{3x}}}{\mpar{s^{2\prime}_1,s_{3x}}}{\alpha^2_{1}}{\beta_{3xj}^{j \in J'_{3x}}}{g_{3x}}{\psi_{3x}} \right)^{x\in X}\]
+
+These two cases define (depending on how $t_{12}$ is built) the family $t_{13x}$ of OTs we are looking for.
+Thus, for both cases we have to prove the following:
+\begin{align*}		
+		&\mpar{\forall x \in X, J'_{13x} \cap H' =
+ J'_{12} \cap H'} \text{ and }\\
+		&  V_{12} \uplus V_{13} \uplus \fvars{t_{13}} \vdash\\ & R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge\\[12pt]
+			g_{13x} \wedge R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
+		\end{array}} 
+	\end{align*}
+
+Recall in this second case, i.e. where only $A_1$ performs a transition $t_{12}$,  $k \notin J^{\prime}_1$, $\forall x \in X$ we have
+\begin{align*}		
+J'_{13x} \cap H' & = J'_{3x}  \cap \mpar{J'_1 \uplus H \setminus \mbrc{k}} \\
+& = \mpar{J'_{3x}\cap H } \text{ since } J'_{3x}\cap J'_1=\emptyset \land k\not\in J'_1 \\
+& = \mpar{J'_2\cap H } \text{  since } J'_2 \cap H = J'_{3x} \cap H\\
+& = \mpar{J'_{12}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'\\
+& \text{\RAB{Pas sure cette derniere etape}}
+\end{align*}
+
+The proof of the rest of the formula follows the same steps as the previous case the only argument that changes is that by composition we obtain:  $g_{12} \Leftrightarrow g_1$ and
+$g_{13x}  \Leftrightarrow g_{1}$.\\
+
+\item Lastly, we have to prove the satisfaction of the deadlock reduction condition, i.e., for all $\mpar{s_{12}, s_{13}} \in S_{12} \times S_{13}$
+\begin{multline*}
+V_{12} \uplus V_{13}  \vdash \\ R\mpar{s_{12}, s_{13}} \nwedge  \neg(\bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}) \implies   \neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})
+\end{multline*}
+
+Let's start  with the hypothesis of the theorem stating that $\wrel{A_2}{A_3}{H}$, thus we have for all  $\mpar{s_2, s_3} \in S_2 \times S_3$ 
+\begin{multline*}
+V_2 \uplus V_3  \vdash R\mpar{s_2, s_3} \nwedge \neg (\bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}) \implies   \neg(\bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3})
+\end{multline*}
+This implies: 
+\begin{multline*}
+V_2 \uplus V_3  \vdash R\mpar{s_2, s_3} \nwedge \neg (\bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}) \vee \neg (\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}) \implies  \\ \neg(\bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3}) \vee \neg (\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1})
+\end{multline*}
+
+\RAB{Trop trivial...}
 ~\qed

### 2023-02-24 2021-Refinement/paper/refinementarticleV2.tex
sketch proof

@@
 
-\subsection{A bisimulation for open automata.}
+\subsection{A bisimulation for open automata}
 
@@
 
-\begin{definition}[Non-blocking composition]
+\begin{definition}[Non-blocking composition] \label{Def:Non-block}
 Let \(A_i = \OAg[i]\) with \( 0 \leq i \leq n\) be a family of open automata.
@@
 \begin{quote}
-Suppose that $\wrel{A_1}{A_2}{H}$, \(k \in H\) \cancel{and that \(A_1\subst{A_3}{k}\) is non-blocking}. We have: 
+Suppose that $\wrel{A_1}{A_2}{H}$, \(k \in H\) and that \(A_1\subst{A_3}{k}\) is non-blocking. We have: 
 \[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{J_3 \uplus H \setminus \mbrc{k}}\]
@@
 
-Let's start  with the hypothesis of the theorem stating that $\wrel{A_1}{A_2}{H}$, thus we have for all  $\mpar{s_1, s_2} \in S_1 \times S_2$ 
+By hypothesis  the second  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Non-block} we have for all state $s_{13}$ which is reachable, i.e.
+$ \fvars{t_{13}}\vdash \reach{A_{13}}\mpar{s_{13}}$,  the following:
+
+\begin{multline*}
+V_{13} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1}  \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}
+\end{multline*}
+From this we can infer:
+\begin{multline*}
+V_{13}  \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash  \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})  \implies   \neg(\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1})
+\end{multline*}
+
+Furthermore, from the second  hypothesis  stating that $\wrel{A_1}{A_2}{H}$,  we have for all  $\mpar{s_1, s_2} \in S_1 \times S_2$ 
 \begin{multline*}
@@
 \end{multline*}
-Because the guards from transitions of $A_1$ are still transitions of $A_{13}$, we get:  
-\begin{multline*}
-V_{13}   \vdash \neg(\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}) \implies \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})
-\end{multline*}
-
-Similarly, transitions of $A_2$ are still transitions of $A_{23}$,  we get:
+
+From the two previous formula can deduce:
+\begin{multline*}
+V_{13} \uplus V_2 \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash\\ R\mpar{s_1, s_2} \nwedge \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})  \implies   \neg(\bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2})
+\end{multline*}
+
+Because the guards from transitions of $A_2$ are still transitions of $A_{23}$,  thus we have:
 \begin{multline*}
@@
 \end{multline*}
-From the three previous formulas we deduce:
-  \begin{multline*}
-V_{13} \uplus V_{23} \vdash R\mpar{s_1, s_2} \nwedge \neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}) \implies   \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
-\end{multline*}
-
-which also implies:
-\begin{multline*}
-V_{13} \uplus V_{23}  \vdash \\ \underbrace{R\mpar{s_1, s_2} \wedge  \mpar{\,\,\bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3 \wedge s^1_3=s^2_3}}_{R^{\prime}(s_{13},s_{23})}  \wedge \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})   \implies \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
-\end{multline*}
-which gives us what we needed to demonstrate. \qed
-
+
+From the two previous formula and by introducing the following tautology\\ $ \mpar{\,\,\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}$, we get:
+\begin{multline*}
+V_{13} \uplus V_{23}  \vdash  \underbrace{R\mpar{s_1, s_2} \wedge  \mpar{\,\,\bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3 \wedge s^1_3=s^2_3}}_{R^{\prime}(s_{13},s_{23})} \wedge \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})   \\ \implies \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
+\end{multline*}
+which gives the expected result. \qed
 \end{enumerate}
@@
 \begin{enumerate}
-\item \TODO{Pareil que le theorem precedent}
+\item \TODO{I skip it, I think the same as previous theorem}
 
@@
 V_{13}= V^2_1\uplus V_3\\
-& H'=H_{23}\uplus J_1 \setminus \{k\} \subseteq J_1\uplus \mpar{J_2 \cap J_3} \setminus \{k\} = \mpar{J^1_1\uplus J_2 \setminus \{k\} } \cap \mpar{J^2_1\uplus J_3 \setminus \{k\}} = J_{12 } \cap J_{13}
+& H'=H_{23}\uplus J_1 \setminus \{k\} \subseteq J_1\uplus \mpar{J_2 \cap J_3} \setminus \{k\}= \mpar{J^1_1\uplus J_2 \setminus \{k\} } \cap \mpar{J^2_1\uplus J_3 \setminus \{k\}} \\ &\,\,\,\, = J_{12 } \cap J_{13}
 \end{align*}
@@
 \begin{multline*}
-V_{12} \uplus V_{13}  \vdash \\ R\mpar{s_{12}, s_{13}} \nwedge  \neg(\bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}) \implies   \neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})
+V_{12} \uplus V_{13}  \vdash  R\mpar{s_{12}, s_{13}} \nwedge  \neg(\bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}) \implies   \neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}) 
 \end{multline*}
@@
 \end{multline*}
-This implies: 
-\begin{multline*}
-V_2 \uplus V_3  \vdash R\mpar{s_2, s_3} \nwedge \neg (\bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}) \vee \neg (\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}) \implies  \\ \neg(\bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3}) \vee \neg (\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1})
-\end{multline*}
-
-\RAB{Trop trivial...}
+
+By adding the same terms to both sides of the implication, we get:
+\begin{multline*}
+V_2 \uplus V_3  \vdash R\mpar{s_2, s_3} \nwedge \neg (\bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}) \vee \neg (\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}) \vee \neg \bigcirc \\ \vspace{4em} \implies   \neg(\bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3})\vee \neg (\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1})\vee \neg \bigcirc
+\end{multline*}
+
+\RAB{On aurait pas envie d'ecrire  l'egalite des actions de trous}
+
 ~\qed

### 2023-02-27 2021-Refinement/paper/refinementarticleV2.tex
proof with reachability

@@
 We define a relation $R'$ relating states of $s_{13}$ and $s_{23}$ as follows:
-\[ R' \mpar{s_{13}, s_{23}} = R\mpar{s_{1}, s_{2}}  %\wedge \reach{A_{13}}\mpar{s_{13}}
+\[ R' \mpar{s_{13}, s_{23}} = R\mpar{s_{1}, s_{2}} \land \reach{A_{13}}(s_{13})  %\wedge \reach{A_{13}}\mpar{s_{13}}
  \wedge \bigwedge_\subbox{v_3\in V_3}
- v^1_3=v^2_3\wedge s^1_3 = s^2_3\]
+ v^1_3=v^2_3\land s^1_3 = s^2_3\]
 
@@
 \end{align*}
+The last step comes from the additional fact that  $\reach{A_{13}}(s_{013})$.
+
 \item Second, we need to prove for any open transition $t_{13}$ in $T_{13}$ originating from $s_{13}$:
@@
 	\end{align*}
+
 Recall that by definition of composition and open automata refinement we have: 
@@
 \begin{enumerate}
-\item  Because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transitions $t_3$ and .
-By construction of  $t_{13}$ and $t_{23x}$ we have $\alpha_{13}=
+\item  By construction of  $t_{13}$ and $t_{23x}$ we have $\alpha_{13}=
 \alpha_{1}$ and $\alpha_{23x}=\alpha_{2x}$. So we deduce: 
@@
 ${\displaystyle V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}} \vdash \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$\\
-The disjunction with the following hypothesis:\\ $V_{1} \uplus V_{2} \uplus \fvars{t_1}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}}$  will give:
+Then we compose by  disjunction with the following hypothesis (part of formula $(*)$).\\ $V_{1} \uplus V_{2} \uplus \fvars{t_1}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}}$
 \begin{align*}
@@
 
-By the extension of the valuation context mentioned above in the formula $(*)$ and by using the statements resulting from the cases (a), (b) and (c), we get:
+We can extend the valuation context of the variables to cover the variables of the transitions $t_3$ and the variables in $V_3^1$ and $V_3^2$ in the formula $(*)$.  
+By   using the statements resulting from the cases (a), (b) and (c), we get:
 \begin{multline*}
@@
 
-\RAB{ I think there is no need to the no blocking condition} Furthermore, by hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have $ \sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ and for all $t_{13} \in T_{13}$:
+ Furthermore, by hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have, for all $t_{13} \in T_{13}$:
 \[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
@@
 V_{13} \uplus V_{23} \uplus \fvars{t_1}  \cap \fvars{t_{13}} \vdash\\
-R\mpar{s_1, s_{2}} \wedge g_{13}  \cancel{\wedge \reach{A_{13}}\mpar{s_{13}}}
+R\mpar{s_1, s_{2}} \wedge g_{13}  {\wedge \reach{A_{13}}\mpar{s_{13}}}
 \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
@@
 			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge 	g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\\
-		  \wedge \cancel{\reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
+		  \wedge {\reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
 \wedge} \bigwedge_\subbox{v_3\in V_3}  \psi_{13}(v^1_3)=\psi_{13}(v^2_3)\wedge s^{1\prime}_3=s^{2\prime}_3
@@
 V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
-R\mpar{s_1, s_{2}} \wedge g_{13} \land \cancel{\reach{A_{13}}\mpar{s_{13}} \land} \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3 \wedge s^1_3 = s^2_3
+R\mpar{s_1, s_{2}} \wedge g_{13} \land {\reach{A_{13}}\mpar{s_{13}} \land} \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3 \wedge s^1_3 = s^2_3
 \implies \hspace{7em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
 \begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\land  \cancel{\reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}}		\nwedge\\
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\land  {\reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}}		\nwedge\\
 			  R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge
@@
 
-These two cases define (depending on how $t_{13}$ is built) the family $t_{23x}$ of OTs we are looking for.
-Thus, for both cases we have to prove the following:
-\begin{align*}		
-		&\mpar{\forall x \in X, J'_{23x} \cap H' =
- J'_{13} \cap H'} \text{ and }\\
-		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ & R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge\\[12pt]
-			g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
-		\end{array}} 
-	\end{align*}
-
-Recall in this second case, i.e. where only $A_1$ performs a transition $t_{13}$,  $k \notin J'_1$, $\forall x \in X$ we have
-\begin{align*}		
-J'_{23x} \cap H' & = J'_{2x}  \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
-& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
-& = \mpar{J'_1\cap H } \text{  since } J'_1 \cap H = J'_{2x} \cap H\\
-& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'
-\end{align*}
-
-The proof of the rest of the formula follows the same steps as the previous case the only argument that changes is that by composition we obtain:  $g_{13} \Leftrightarrow g_1$ and
-$g_{23x}  \Leftrightarrow g_{2x}$.\\
-
-\item \TODO{To check from this point:} Lastly, we have to prove the satisfaction of the deadlock reduction condition, i.e., for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
+\TODO{do this case: the following is old text that makes no sense}
+Principle:
+\TODO{The proof of the rest of the formula follows the same steps as the previous case the only argument that changes is that by composition we obtain:  $g_{13} \Leftrightarrow g_1$ and $g_{23x}  \Leftrightarrow g_{2x}$}
+%
+%These two cases define (depending on how $t_{13}$ is built) the family $t_{23x}$ of OTs we are looking for.
+%Thus, for both cases we have to prove the following:
+%\begin{align*}		
+%		&\mpar{\forall x \in X, J'_{23x} \cap H' =
+% J'_{13} \cap H'} \text{ and }\\
+%		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ & R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+%			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge\\[12pt]
+%			g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
+%		\end{array}} 
+%	\end{align*}
+%	
+%Recall in this second case, i.e. where only $A_1$ performs a transition $t_{13}$,  $k \notin J'_1$, $\forall x \in X$ we have
+%\begin{align*}		
+%J'_{23x} \cap H' & = J'_{2x}  \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
+%& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
+%& = \mpar{J'_1\cap H } \text{  since } J'_1 \cap H = J'_{2x} \cap H\\
+%& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'
+%\end{align*}
+%
+%The proof of the rest of the formula follows the same steps as the previous case the only argument that changes is that by composition we obtain:  $g_{13} \Leftrightarrow g_1$ and
+%$g_{23x}  \Leftrightarrow g_{2x}$.\\
+
+\item Lastly, we have to prove the satisfaction of the deadlock reduction condition, i.e., for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
 \begin{multline*}
@@
 
-By hypothesis  the second  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Non-block} we have for all state $s_{13}$ which is reachable, i.e.
-$ \fvars{t_{13}}\vdash \reach{A_{13}}\mpar{s_{13}}$,  the following:
-
-\begin{multline*}
-V_{13} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1}  \vdash \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}
+By hypothesis  the composition  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Non-block} we have for all state $s_{13}$:
+
+\begin{multline*}
+V_{13} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1}  \vdash  \left(\reach{A_{13}(s_{13})} \land \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}\right) \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}
 \end{multline*}
@@
 \begin{multline*}
-V_{13}  \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash  \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})  \implies   \neg(\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1})
+V_{13}  \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash  \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})  \implies   \neg(\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}) \lor
+\neg{\reach{A_{13}(s_{13})}}
 \end{multline*}
@@
 V_{13} \uplus V_2 \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash\\ R\mpar{s_1, s_2} \nwedge \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})  \implies   \neg(\bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2})
-\end{multline*}
-
-Because the guards from transitions of $A_2$ are still transitions of $A_{23}$,  thus we have:
+\lor \neg{\reach{A_{13}}(s_{13}) }
+\end{multline*}
+
+By definition of the composition of open automata, each guard of automaton 
+ $A_{23}$ is of the form $\fguard{t_{23}} = \fguard{t_{2}}\land t$,  thus we have:
 \begin{multline*}
@@
 
-From the two previous formula and by introducing the following tautology\\ $ \mpar{\,\,\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}$, we get:
-\begin{multline*}
-V_{13} \uplus V_{23}  \vdash  \underbrace{R\mpar{s_1, s_2} \wedge  \mpar{\,\,\bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3 \wedge s^1_3=s^2_3}}_{R^{\prime}(s_{13},s_{23})} \wedge \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})   \\ \implies \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
+From the two previous formula and by introducing the following tautology\\ $ \mpar{\,\,\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}$, we get: \TODO{faire une jolie equation}
+\begin{multline*}
+V_{13} \uplus V_{23}  \vdash  \underbrace{R\mpar{s_1, s_2} \wedge \reach{A_{13}}(s_{13}) \land \mpar{\,\,\bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3 \wedge s^1_3=s^2_3}}_{R^{\prime}(s_{13},s_{23})} \wedge \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})   \\ \implies \left(\neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}) \lor \neg{\reach{A_{13}}(s_{13}) }\right) \land \reach{A_{13}}(s_{13})\\
+\implies \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
 \end{multline*}
@@
 \section{Proof of Congruence}
-Suppose $\wrel{A_2}{A_3}{H}$ and  $k \in H$. We have: \[\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{J_1 \uplus H \setminus \mbrc{k}}\]
+Suppose $\wrel{A_2}{A_3}{H}$ and  $k \in H$.  and the composition $A_1\subst{A_2}{k}$ is non-blocking. We have: \[\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{J_1 \uplus H \setminus \mbrc{k}}\]
 \proof
@@
 Let us denote with $t^2$ and $t^3$  the elements of $A_2$ and $A_3$ respectively.
-Consider any two states $s_{12} = \mpar{s_1,s^1_2}$ and $s_{13} = \mpar{s^2_1,s_3}$ ($s^1_1$ and $s^2_1$  are the same with renaming).
+Consider any two states $s_{12} = \mpar{s^1_1,s_2}$ and $s_{13} = \mpar{s^2_1,s_3}$ ($s^1_1$ and $s^2_1$  are the same with renaming).
 We define a relation $R'$ relating states of $s_{12}$ and $s_{13}$ as follows:
-\[ R' \mpar{s_{12}, s_{13}} = R\mpar{s_{2}, s_{2}} \wedge \bigwedge_\subbox{v_1\in V_1}
+\[ R' \mpar{s_{12}, s_{13}} = R\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1}
  v^1_1=v^2_1\wedge s^1_1 = s^2_1\]
@@
 \end{align*}
-there exists an indexed family of OTs originating from $s_{2}$: 
+there exists an indexed family of OTs originating from $s_{3}$: 
 \begin{align*}
@@
 We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (as stated above).
-By hypothesis we have $k \in H$, so in the case where $k \in {J^1_{1}}^{\prime}$, we deduce that $k \in J'_{3x}$ we can  then build  a family of OTs $t_{13x}^{x\in X}$ with the same transitions of $A_1$ (up to renaming) as those used to build $t_{12}$.
+By hypothesis we have $k \in H$, so in the case where $k \in {J^1_{1}}^{\prime}$, we deduce that $k \in J'_{3x}$ we can  then build  a family of OTs $t_{13x}^{x\in X}$ with the same transitions as $A_1$ (up to renaming) as those used to build $t_{12}$.
 \[
@@
 \begin{enumerate}
-\item  Because composition doesn't change the resulting actions, nor their variables, we can extend the valuation context of the variables to cover the variables of the transitions $t_2$ and $t_{3x}$.
-By construction of  $t_{12}$ and $t_{13x}$ we have $\alpha_{12}=
-\alpha^1_{1}$ and $\alpha_{13x}=\alpha^2_{1}$. Since  $\alpha^1_{1}$ and  $\alpha^2_{1}$ are the same (up the renaming. So we deduce: 
+\item     By construction of  $t_{12}$ and $t_{13x}$ we have $\alpha_{12}=
+\alpha^1_{1}$ and $\alpha_{13x}=\alpha^2_{1}$. Since  $\alpha^1_{1}$ and  $\alpha^2_{1}$ are the same (up to renaming) we deduce: 
 $\alpha_{12} = \alpha_{13x}$.
@@
 ${\displaystyle V^1_{1} \uplus V^2_{1} \uplus \fvars{t_{12}} \vdash \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1\implies \bigwedge_\subbox{j \in J^{2 \prime}_1} \beta^1_{1j}= \beta^2_{1j}}$\\
-The disjunction with the following hypothesis:\\ $V_{2} \uplus V_{3} \uplus \fvars{t_2}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj}}$  will give:
+We compose by disjunction with the following hypothesis (part of formula $(*)$).\\ $V_{2} \uplus V_{3} \uplus \fvars{t_2}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj}}$
 \begin{align*}
@@
 
-By the extension of the valuation context mentioned above in the formula $(*)$ and by using the statements resulting from the cases (a), (b) and (c), we get:
-\begin{multline*}
-V_{13} \uplus V_{23}  \uplus \fvars{t_{13}} \vdash\\
+We can extend the valuation context of the variables to cover the variables of the transitions $t_1$ and variables $V_1^1$ and $V_1^2$ in the formula $(*)$.
+By using the statements resulting from the cases (a), (b) and (c), we get:
+\begin{multline*}
+V_{13} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash\\
 R\mpar{s_2, s_{3}} \wedge \mpar{g_2 \wedge g^1_1 \wedge \alpha^1_1=\beta_{2k}}\wedge \bigwedge_\subbox{v_1\in V_1}  v^1_1=v^2_1 %\wedge s^1_1=s^2_1
@@
 \begin{multline*}
-V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
+V_{12} \uplus V_{13} \uplus \fvars{t_{12}}  \vdash\\
 R\mpar{s_2, s_{3}} \wedge g_{12}  \land \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1
@@
 
+ Furthermore, by hypothesis we have  \(A_1\subst{A_2}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have, for all $t_{12} \in T_{12}$:
+\[ \fvars{t_{12}} \vdash \left(\reach{A_{12}}\mpar{s_{12}} \wedge g_{12} \implies \reach{A_{12}}\mpar{s_{12}'}\psubst{\psi_{12}}\right) \]
+
+Thus, we get:
+\begin{multline*}
+V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash\\
+R\mpar{s_2, s_{3}} \wedge g_{12} \land \reach{A_{12}}\mpar{s_{12}} \land \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1  \wedge s^1_1 = s^2_1 
+\implies \hspace{12em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge g_{13x} \wedge \\
+			 R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}} \land \reach{A_{12}}\mpar{s_{12}'}\psubst{\psi_{12}} \\
+\wedge \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{12}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1
+		\end{array}}   
+\end{multline*}
+
 Because of the independence of the substitution domains, we simplify and get the expected formula:
@@
 			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge g_{13x} \wedge 
-			 R\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
+			 R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
 		\end{array}}   
@@
 
+\TODO{a refaire a partir d ici}
 These two cases define (depending on how $t_{12}$ is built) the family $t_{13x}$ of OTs we are looking for.
@@
 \begin{multline*}
-V_{12} \uplus V_{13}  \vdash  R\mpar{s_{12}, s_{13}} \nwedge  \neg(\bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}) \implies   \neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}) 
+V_{12} \uplus V_{13}  \vdash  R'\mpar{s_{12}, s_{13}} \nwedge  \neg(\bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}) \implies   \neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})
 \end{multline*}
@@
 
-By adding the same terms to both sides of the implication, we get:
-\begin{multline*}
-V_2 \uplus V_3  \vdash R\mpar{s_2, s_3} \nwedge \neg (\bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}) \vee \neg (\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}) \vee \neg \bigcirc \\ \vspace{4em} \implies   \neg(\bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3})\vee \neg (\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1})\vee \neg \bigcirc
-\end{multline*}
-
-\RAB{On aurait pas envie d'ecrire  l'egalite des actions de trous}
-
-~\qed
+By hypothesis  the composition  \(A_1\subst{A_2}{k}\) is non-blocking,  then according to the Definition \ref{Def:Non-block} we have for all state $s_{12}$:
+
+\begin{multline*}
+V_{12} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1}  \vdash  \left(\reach{A_{12}(s_{12})} \land \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}\right) \implies \bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}
+\end{multline*}
+
+Which implies 
+\begin{multline*}
+V_{12} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1}  \vdash 
+\neg{ \bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}}
+\implies 
+\left(\neg{\reach{A_{12}(s_{12})} }\lor \neg{\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
+\right)
+\end{multline*}
+
+Additionally, each transition $t_{13}$ of $OT(s_{13})$ is of the form $
+g_1\land g_3 \land g$ with $g_1$ a guard of a transition $t_{1}$ of $OT(s_{1})$.
+Thus 
+\[
+\neg{\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}  \implies \neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}) \]
+
+Thus we have, as $R$ contains the reachability of state $S_{12}$:\TODO{faire une jolie equation}
+\begin{multline*}
+V_{12} \uplus V_{13}  \vdash  R'\mpar{s_{12}, s_{13}} \nwedge  \neg(\bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}) \\
+\implies \reach{A_{12}(s_{12})} \land \left(\neg{\reach{A_{12}(s_{12})} }\lor
+\neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})\right) \\
+\implies
+\neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})
+\end{multline*}
+\qed
+
 \end{enumerate}

### 2023-02-27 2021-Refinement/paper/refinementarticleV2.tex
todos and small changes

@@
 \title{Refinements for open automata}
+
 %
@@
 \section{Introduction}
+
+\TODO{TODO list}
+
+* case 2 of the proofs for both theorems
+
+* example
+
+* positioning
+
+* global rewriting
 
@@
    \caption{Open Automaton. It exposes an unspecified counter in the "cnt" hole
- to count external tick actions. The system sets a counter when a query is enabled and updates  when  the time is over.\label{Fig:SpecOA}}
+ to count external tick actions.
+The system sets a counter when a query is enabled and updates  when  the time is over.\label{Fig:SpecOA}} \TODO{refaire l exemple pour l instant il a pas vraiment de sens}
 \end{figure}
@@
 This relation thus focuses on the simulation of transitions and uses the previous definition to prevent the refined automaton from non-deterministically reaching states that introduce deadlocks in a scenario planned without deadlock in the specification.
-\TODO{Changement de la definition de simulation pour selon la simulation de Olga}
 
@@
 
-\TODO{To discuss this definition}
-
 Note in this definition, instead of matching an instantiated transition (with all variables assigned) of the first automata to another instantiated transition of the second, it matches an open transition $t_1$ to a family of covering open transitions $t_{2x}^{x\in X}$.
@@
 
+\TODO{remove this def}
 \begin{definition}[Deadlock reduction]\label{def:dpwd}\\
@@
 
-\TODO{Fin reintroduction}
+\subsection{Automaton refinement}
 
@@
 Let $J_3$ be the set of holes of $A_3$ and suppose that $k \in H$.
-%Suppose that \(k \in H\) and that \(A_1\subst{A_3}{k}\) is non-blocking.
+Suppose that \(k \in H\) and that \(A_1\subst{A_3}{k}\) is non-blocking.
 We have: \[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{J_3 \uplus H \setminus \mbrc{k}}\]
 \end{theorem}
-\RAB{A t-on des conditions sur H?}
 
@@
 Let $A_1$, $A_2$ and $A_3$ be three open automata with $\wrel{A_2}{A_3}{H}$. 
- $\wrel{A_1}{A_2}{H}$.  Let $J_3$ be the set of holes of $A_3$ and suppose that \(k \in H\).
+  Let $J_3$ be the set of holes of $A_3$ and suppose that \(k \in H\). Suppose additionally that the composition $A_1\subst{A_2}{k}$ is non-blocking.
 We have: \[\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{J_1 \uplus H \setminus \mbrc{k}}\]
@@
 
-\begin{example} \RAB{cet exemple illustre plutot  que la composition est un raffinement, i.e.,  $\wrel{A_1\subst{A_2}{k}}{A_1}{J_1   \setminus \mbrc{k}}$ doit-on ajouter ce resultat comme un lemme?}
+\begin{example}
 

### 2023-03-01 2021-Refinement/paper/refinementarticleV2.tex
second case context refinement

@@
 \]
-We then obtain a family of OTs by the simulation of $A_1$ by $A_2$ (stated above).
-As  $k \in H$ we have $k \not\in J'_{2x}$ and we build:
+As stated above, from the simulation of $A_1$ by $A_2$ we get a  family of OTs $t_{2x}^{x\in X}$. The composition of this family of OTs 
+ with the same transitions of $A_3$ (up to renaming) as those used to build $t_{13}$ 
+produces  a family of OTs $t_{23x}^{x\in X}$ in the form:
 \[t_{23x} = \left(
@@
 
-\TODO{do this case: the following is old text that makes no sense}
-Principle:
-\TODO{The proof of the rest of the formula follows the same steps as the previous case the only argument that changes is that by composition we obtain:  $g_{13} \Leftrightarrow g_1$ and $g_{23x}  \Leftrightarrow g_{2x}$}
+By hypothesis we have   $k \in H$, since $k \not\in J'_{1}$,  we deduce $k \not\in J'_{2x}$. \\
+$\forall x \in X$ we have:
+\begin{align*}		
+J'_{23x} \cap H' & = J'_{2x}  \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
+& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
+& = \mpar{J'_1\cap H } \text{  since } J'_1 \cap H = J'_{2x} \cap H\\
+& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'
+\end{align*}
+
+The proof of the rest of the formula follows the same steps as the previous case the only argument that change is that by composition we obtain:  $g_{13} \Leftrightarrow g_1$ and $g_{23x}  \Leftrightarrow g_{2x}$ and the actions of $\alpha_{13}$ and $\alpha_{23x}$ are renaming of  $\alpha_{1}$ and $\alpha_{2x}$ resp.
+The same for $\beta_{13j}$ and $\beta_{23xj}$ that are renaming of $\beta_{1j}$ and $\beta_{2xj}$ resp.
+
+\TODO{Redone! To check}
+
 %
@@
 V_{13}= V^2_1\uplus V_3\\
-& H'=H_{23}\uplus J_1 \setminus \{k\} \subseteq J_1\uplus \mpar{J_2 \cap J_3} \setminus \{k\}= \mpar{J^1_1\uplus J_2 \setminus \{k\} } \cap \mpar{J^2_1\uplus J_3 \setminus \{k\}} \\ &\,\,\,\, = J_{12 } \cap J_{13}
+& H'=H\uplus J_1 \setminus \{k\} \subseteq J_1\uplus \mpar{J_2 \cap J_3} \setminus \{k\}= \mpar{J^1_1\uplus J_2 \setminus \{k\} } \cap \mpar{J^2_1\uplus J_3 \setminus \{k\}} \\ &\,\,\,\, = J_{12 } \cap J_{13}
 \end{align*}
@@
 \begin{align*}
-  J'_{31x} \cap H'  
+  J'_{13x} \cap H'  
 &=((J'_{3x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{1} ) \cap (H\uplus J_1 \setminus\{k\} )\\
@@
 \]
-We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (stated above).
-As  $k \in H$ we have $k \not\in J^{1\prime}_1$ and we build:
-\[t_{13x} = \left(
-\OT{\mpar{s^2_1, s_{3x}}}{\mpar{s^{2\prime}_1,s_{3x}}}{\alpha^2_{1}}{\beta_{3xj}^{j \in J'_{3x}}}{g_{3x}}{\psi_{3x}} \right)^{x\in X}\]
-
-\TODO{a refaire a partir d ici}
-These two cases define (depending on how $t_{12}$ is built) the family $t_{13x}$ of OTs we are looking for.
-Thus, for both cases we have to prove the following:
-\begin{align*}		
-		&\mpar{\forall x \in X, J'_{13x} \cap H' =
- J'_{12} \cap H'} \text{ and }\\
-		&  V_{12} \uplus V_{13} \uplus \fvars{t_{13}} \vdash\\ & R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge\\[12pt]
-			g_{13x} \wedge R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
-		\end{array}} 
-	\end{align*}
-
-Recall in this second case, i.e. where only $A_1$ performs a transition $t_{12}$,  $k \notin J^{\prime}_1$, $\forall x \in X$ we have
-\begin{align*}		
-J'_{13x} \cap H' & = J'_{3x}  \cap \mpar{J'_1 \uplus H \setminus \mbrc{k}} \\
-& = \mpar{J'_{3x}\cap H } \text{ since } J'_{3x}\cap J'_1=\emptyset \land k\not\in J'_1 \\
-& = \mpar{J'_2\cap H } \text{  since } J'_2 \cap H = J'_{3x} \cap H\\
-& = \mpar{J'_{12}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'\\
-& \text{\RAB{Pas sure cette derniere etape}}
-\end{align*}
-
-The proof of the rest of the formula follows the same steps as the previous case the only argument that changes is that by composition we obtain:  $g_{12} \Leftrightarrow g_1$ and
-$g_{13x}  \Leftrightarrow g_{1}$.\\
+As stated above, from the simulation of $A_2$ by $A_3$ we get a  family of OTs $t_{3x}^{x\in X}$. The composition of this family of OTs 
+ with the same transitions of $A_1$ (up to renaming) as those used to build $t_{12}$ 
+produces  a family of OTs $t_{13x}^{x\in X}$ in the form:
+\[t_{13x} = \left(\OT{\mpar{s^2_1, s_{3}}}  {\mpar{s^{2\prime}_1, s_{3x}}}  {\alpha_1^2}{{(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{ g^2_1 }{\psi^2_1} \right) \]
+
+$\forall x \in X$ we have
+\begin{align*}		
+J'_{13x} \cap H' & =  J^{2 \prime}_1 \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \\
+& =  J^{1 \prime}_1 \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \text{ since }  J^{2 \prime}_1 =  J^{1 \prime}_1\\
+& = \mpar{J'_{12}\cap H' }
+\end{align*}
+
+By hypothesis we have   $k \in H$ and $k \not\in J^{1\prime}_1$, then $k \not\in J^{2\prime}_1$.
+
+ \TODO{I will continue...}
 
@@
 
-Additionally, each transition $t_{13}$ of $OT(s_{13})$ is of the form $
-g_1\land g_3 \land g$ with $g_1$ a guard of a transition $t_{1}$ of $OT(s_{1})$.
+Additionally, each transition $t_{13}$ of OT$(s_{13})$ is of the form $
+g_1\land g_3 \land g$ with $g_1$ a guard of a transition $t_{1}$ of OT$(s_{1})$.
 Thus 

### 2023-03-03 2021-Refinement/paper/refinementarticleV2.tex
congruence in progress

@@
 
+For this case, the  composition doesn't change the produced actions nor its variables, we have:  $g_{12} \Leftrightarrow g^1_1$ and $g_{13x}  \Leftrightarrow g^2_1$ and the actions of $\alpha_{12}= \alpha^1_1$ and $\alpha_{23x} = = \alpha^2_1$ and the actions of the holes in $J_{13}$ coincide by the composition.
+
+The same for $\beta_{13j}$ and $\beta_{23xj}$ that are renaming of $\beta_{1j}$ and $\beta_{2xj}$ resp.
+
 By hypothesis we have   $k \in H$ and $k \not\in J^{1\prime}_1$, then $k \not\in J^{2\prime}_1$.
-
- \TODO{I will continue...}
 
@@
 
-Thus we have, as $R$ contains the reachability of state $S_{12}$:\TODO{faire une jolie equation}
+Thus we have, as $R$ contains the reachability of state $s_{12}$:\TODO{faire une jolie equation}
 \begin{multline*}

### 2023-03-08 2021-Refinement/paper/refinementarticleV2.tex
case 2 -- Congruence

@@
 
-For this case, the  composition doesn't change the produced actions nor its variables, we have:  $g_{12} \Leftrightarrow g^1_1$ and $g_{13x}  \Leftrightarrow g^2_1$ and the actions of $\alpha_{12}= \alpha^1_1$ and $\alpha_{23x} = = \alpha^2_1$ and the actions of the holes in $J_{13}$ coincide by the composition.
-
-The same for $\beta_{13j}$ and $\beta_{23xj}$ that are renaming of $\beta_{1j}$ and $\beta_{2xj}$ resp.
-
-By hypothesis we have   $k \in H$ and $k \not\in J^{1\prime}_1$, then $k \not\in J^{2\prime}_1$.
+For this case, the  composition doesn't change the produced actions nor its variables, we have:  $g_{12} \Leftrightarrow g^1_1$, $g_{13x}  \Leftrightarrow g^2_1$, $\alpha_{12}= \alpha^1_1$ and $\alpha_{23x} =  \alpha^2_1$.
+Furthermore, we have the actions of the holes in $J_{13}$ coincide by the composition, $\beta_{13j}$ and $\beta_{23xj}$  are renaming of $\beta_{1j}$ and $\beta_{2xj}$ resp.
+
+\TODO{D'apres l'hypothese de depart, la formule (*) nous obtenons une formule sous cette forme: $R\mpar{s_2, s_3} \wedge g_2 \implies R\mpar{s'_2, s'_{3x}}$  l'idee est de faire disparaitre g2.
+On a la formule suivante:}
+
+According to the relation between $A_2$ and $A_3$ open automata,  for all $\mpar{s_2, s_{3}} \in S_2\times S_3$  we have:
+\begin{multline*}
+ V_2 \uplus V_3  \vdash R\mpar{s_2, s_3} \wedge \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} )\implies \lnot( \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3}  )
+\end{multline*}
+
+\TODO{La conjonction des deux donne $False \implies R\mpar{s'_2, s'_{3x}}$ qui true???}
+
+%By hypothesis we have   $k \in H$ and $k \not\in J^{1\prime}_1$, then $k \not\in J^{2\prime}_1$.
 

### 2023-03-09 2021-Refinement/paper/refinementarticleV2.tex
proofs small things

@@
 
- Furthermore, by hypothesis we have  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have, for all $t_{13} \in T_{13}$:
+ Furthermore,  according to the Definition \ref{Def:Reach} (reachability applied to the composed automaton ${A_1\subst{A_3}{k}}$) we have, for all $t_{13} \in T_{13}$:
 \[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
@@
 
-The proof of the rest of the formula follows the same steps as the previous case the only argument that change is that by composition we obtain:  $g_{13} \Leftrightarrow g_1$ and $g_{23x}  \Leftrightarrow g_{2x}$ and the actions of $\alpha_{13}$ and $\alpha_{23x}$ are renaming of  $\alpha_{1}$ and $\alpha_{2x}$ resp.
-The same for $\beta_{13j}$ and $\beta_{23xj}$ that are renaming of $\beta_{1j}$ and $\beta_{2xj}$ resp.
-
-\TODO{Redone! To check}
+The proof of the rest of the formula follows the same steps as the previous case the only argument that change is that by composition we obtain:  $g_{13} $ is the same as $ g_1$ and $g_{23x}$  is the same as $g_{2x}$ and the actions of $\alpha_{13}$, resp.
+$\alpha_{23x}$, is the same as  $\alpha_{1}$, resp.
+$\alpha_{2x}$.
+Similarly $\beta_{13j}$ and $\beta_{23xj}$ that are the same as $\beta_{1j}$ and $\beta_{2xj}$ respectively.
+ We also apply the reachability definition but only on the automaton $A_1$
 
@@
 
- Furthermore, by hypothesis we have  \(A_1\subst{A_2}{k}\) is non-blocking,  then according to the Definition \ref{Def:Reach} we have, for all $t_{12} \in T_{12}$:
+ Furthermore, according to the Definition \ref{Def:Reach} (reachability, applied to the composed automaton \(A_1\subst{A_2}{k}\)) we have, for all $t_{12} \in T_{12}$:
 \[ \fvars{t_{12}} \vdash \left(\reach{A_{12}}\mpar{s_{12}} \wedge g_{12} \implies \reach{A_{12}}\mpar{s_{12}'}\psubst{\psi_{12}}\right) \]

### 2023-03-09 2021-Refinement/paper/refinementarticleV2.tex
point dsicute ce matin

@@
 V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash\\
-\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1  \wedge s^1_1 = s^2_1 \implies \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{12}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1 
+\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1  \wedge s^1_1 = s^2_1 \implies \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{13x}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1 
 \end{multline*}
@@
 			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge g_{13x} \wedge \\
-			 R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}} \wedge \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{12}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1
+			 R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}} \wedge \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{13x}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1
 		\end{array}}   
@@
 			 R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}} \land \reach{A_{12}}\mpar{s_{12}'}\psubst{\psi_{12}} \\
-\wedge \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{12}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1
+\wedge \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{13x}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1
 		\end{array}}   
@@
 V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash
-R\mpar{s_{12}, s_{13}} \wedge g_{12} 
+R'\mpar{s_{12}, s_{13}} \wedge g_{12} 
 \implies \hspace{10em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
@@
 produces  a family of OTs $t_{13x}^{x\in X}$ in the form:
-\[t_{13x} = \left(\OT{\mpar{s^2_1, s_{3}}}  {\mpar{s^{2\prime}_1, s_{3x}}}  {\alpha_1^2}{{(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{ g^2_1 }{\psi^2_1} \right) \]
+\[t_{13x} = \left(\OT{\mpar{s^2_1, s_{3}}}  {\mpar{s^{2\prime}_1, s_{3}}}  {\alpha_1^2}{{(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{ g^2_1 }{\psi^2_1} \right) \]
 
@@
 
-For this case, the  composition doesn't change the produced actions nor its variables, we have:  $g_{12} \Leftrightarrow g^1_1$, $g_{13x}  \Leftrightarrow g^2_1$, $\alpha_{12}= \alpha^1_1$ and $\alpha_{23x} =  \alpha^2_1$.
-Furthermore, we have the actions of the holes in $J_{13}$ coincide by the composition, $\beta_{13j}$ and $\beta_{23xj}$  are renaming of $\beta_{1j}$ and $\beta_{2xj}$ resp.
-
-\TODO{D'apres l'hypothese de depart, la formule (*) nous obtenons une formule sous cette forme: $R\mpar{s_2, s_3} \wedge g_2 \implies R\mpar{s'_2, s'_{3x}}$  l'idee est de faire disparaitre g2.
-On a la formule suivante:}
-
-According to the relation between $A_2$ and $A_3$ open automata,  for all $\mpar{s_2, s_{3}} \in S_2\times S_3$  we have:
-\begin{multline*}
- V_2 \uplus V_3  \vdash R\mpar{s_2, s_3} \wedge \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} )\implies \lnot( \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3}  )
-\end{multline*}
-
-\TODO{La conjonction des deux donne $False \implies R\mpar{s'_2, s'_{3x}}$ qui true???}
+\medskip
+\TODO{To check form this point}
+
+We have for all $\mpar{s_{2}, s_{3}} \in S_{2} \times S_{3}$ such that $\reach{A_{12}}(s_{12})$ is satisfiable:
+\begin{align*}
+ R\mpar{s_{2}, s_{3}} &\implies  R\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge s^1_1 = s^2_1 \\
+ & \implies
+R' \mpar{s_{12}, s_{13}}
+\end{align*}
+
+Since in this case the state $s'_{12}$ is the same as $s_{12}$ and $s'_{13x}$ is the same as $s_{13}$, we get:
+\begin{align*}
+ R\mpar{s_{2}, s_{3}}  & \implies
+R' \mpar{s_{12}, s_{13}}\\
+& \implies
+R' \mpar{s'_{12}, s'_{13x}}
+\end{align*}
+Furthermore for this case, the  composition doesn't change the produced actions nor its variables, we have:  $g_{12}$ is the same as $ g^1_1$, $g_{13x}$    as $g^2_1$, $\alpha_{12}$ as $\alpha^1_1$ and $\alpha_{23x}$ as  $\alpha^2_1$.
+Similarly,
+$\beta_{13j}$ and $\beta_{23xj}$ are the same as $\beta_{1j}$ and $\beta_{2xj}$ respectively.\\
+
+Moreover, we have  for any transition $t_1$ in $A_1$ that is used to build $t_{12}$ and $t_{13x}$ the following:
+\begin{multline*}
+V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash\\
+\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1  \wedge s^1_1 = s^2_1 \implies \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{13x}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1 
+\end{multline*}
+
+From the above we can deduce the expected formula:
+\begin{multline*}
+V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash
+R'\mpar{s_{12}, s_{13}} \wedge g_{12} 
+\implies \hspace{10em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+\begin{array}{l}
+			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge g_{13x} \wedge 
+			 R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
+		\end{array}}   
+\end{multline*}
 

### 2023-03-09 2021-Refinement/paper/refinementarticleV2.tex
point dsicute ce matin with no change
new proof sketch

@@
 
-Moreover, we have  for any transition $t_3$ in $A_3$ relying $s_3$ and $s^{\prime}_3$ the following:
+Moreover, we have  for any transition $t_3$ in $A_3$ relating $s_3$ and $s^{\prime}_3$ the following:
 \begin{multline*}
@@
 We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (as stated above).
-By hypothesis we have $k \in H$, so in the case where $k \in {J^1_{1}}^{\prime}$, we deduce that $k \in J'_{3x}$ we can  then build  a family of OTs $t_{13x}^{x\in X}$ with the same transitions as $A_1$ (up to renaming) as those used to build $t_{12}$.
+By hypothesis we have $k \in H$, so in the case where $k \in {J^1_{1}}^{\prime}$, we deduce that $k \in J'_{3x}$ we can  then build  a family of OTs $t_{13x}^{x\in X}$ with the same transition, up to renaming, as the one used to build $t_{12}$ (i.e.
+$t_1^1$), where ${s^2_{1}}^\prime$ is the same as ${s^1_{1}}^\prime$ up to renaming.
 \[
@@
 
-Moreover, we have  for any transition $t_1 $ in $A_1$ relying $s_3$ and $s^{\prime}_1$ the following:
+Moreover, we have  for any transition $t_1 $ in $A_1$ relating $s^1_1$ and ${s^1_1}^{\prime}$ the following:
 \begin{multline*}
@@
 \]
-As stated above, from the simulation of $A_2$ by $A_3$ we get a  family of OTs $t_{3x}^{x\in X}$. The composition of this family of OTs 
- with the same transitions of $A_1$ (up to renaming) as those used to build $t_{12}$ 
-produces  a family of OTs $t_{13x}^{x\in X}$ in the form:
-\[t_{13x} = \left(\OT{\mpar{s^2_1, s_{3}}}  {\mpar{s^{2\prime}_1, s_{3}}}  {\alpha_1^2}{{(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{ g^2_1 }{\psi^2_1} \right) \]
-
-$\forall x \in X$ we have
-\begin{align*}		
-J'_{13x} \cap H' & =  J^{2 \prime}_1 \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \\
-& =  J^{1 \prime}_1 \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \text{ since }  J^{2 \prime}_1 =  J^{1 \prime}_1\\
-& = \mpar{J'_{12}\cap H' }
-\end{align*}
-
-\medskip
-\TODO{To check form this point}
-
-We have for all $\mpar{s_{2}, s_{3}} \in S_{2} \times S_{3}$ such that $\reach{A_{12}}(s_{12})$ is satisfiable:
-\begin{align*}
- R\mpar{s_{2}, s_{3}} &\implies  R\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge s^1_1 = s^2_1 \\
- & \implies
-R' \mpar{s_{12}, s_{13}}
-\end{align*}
-
-Since in this case the state $s'_{12}$ is the same as $s_{12}$ and $s'_{13x}$ is the same as $s_{13}$, we get:
-\begin{align*}
- R\mpar{s_{2}, s_{3}}  & \implies
-R' \mpar{s_{12}, s_{13}}\\
-& \implies
-R' \mpar{s'_{12}, s'_{13x}}
-\end{align*}
-Furthermore for this case, the  composition doesn't change the produced actions nor its variables, we have:  $g_{12}$ is the same as $ g^1_1$, $g_{13x}$    as $g^2_1$, $\alpha_{12}$ as $\alpha^1_1$ and $\alpha_{23x}$ as  $\alpha^2_1$.
-Similarly,
-$\beta_{13j}$ and $\beta_{23xj}$ are the same as $\beta_{1j}$ and $\beta_{2xj}$ respectively.\\
-
-Moreover, we have  for any transition $t_1$ in $A_1$ that is used to build $t_{12}$ and $t_{13x}$ the following:
+%As stated above, from the simulation of $A_2$ by $A_3$ we get a  family of OTs $t_{3x}^{x\in X}$. The composition of this family of OTs 
+% with the same transitions of $A_1$ (up to renaming) as those used to build $t_{12}$ 
+%produces  a family of OTs $t_{13x}^{x\in X}$ in the form:
+%\[t_{13x} = \left(\OT{\mpar{s^2_1, s_{3}}}  {\mpar{s^{2\prime}_1, s_{3}}}  {\alpha_1^2}{{(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{ g^2_1 }{\psi^2_1} \right) \]
+
+\TODO{NEW -- a refaire en plus joli}
+
+Because the hole is not involved we can define (where elements of $A_1$ are the same as above modulo renaming of variables):
+\[t_{13} = \OT{\mpar{s^1_1, s_3}}{\mpar{{s^2_1}', s_3}}{\alpha_1^2}{ {(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{g^2_1}{\psi^2_1}
+\]
+
+% 
+%$\forall x \in X$ we have
+%\begin{align*}		
+%J'_{13x} \cap H' & =  J^{2 \prime}_1 \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \\
+%& =  J^{1 \prime}_1 \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \text{ since }  J^{2 \prime}_1 =  J^{1 \prime}_1\\
+%& = \mpar{J'_{12}\cap H' }
+%\end{align*}
+
+We have by definition 
+\[R' \mpar{s_{12}, s_{13}} =  R\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge s^1_1 = s^2_1 \]
+Thus, because transitions are the same:
+\[R' \mpar{s_{12}, s_{13}} \implies
+R\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge {s^1_1}^\prime = {s^2_1}^\prime
+\]
+
+Moreover, we have  the following:
 \begin{multline*}
 V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash\\
-\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1  \wedge s^1_1 = s^2_1 \implies \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{13x}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1 
-\end{multline*}
+\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1  \wedge s^1_1 = s^2_1 \implies \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{13}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1 
+\end{multline*}
+
+ Furthermore, according to the Definition \ref{Def:Reach} (reachability, applied to the composed automaton \(A_1\)) we have, for all $t_{12} \in T_{12}$:
+\[ \fvars{t_{12}} \vdash \left(\reach{A_{12}}\mpar{s_{12}} \wedge g_{12} \implies \reach{A_{12}}\mpar{s_{12}'}\psubst{\psi_{12}}\right) \]
 
@@
 \begin{array}{l}
-			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge g_{13x} \wedge 
-			 R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
+			\alpha_{12} = \alpha_{13} \wedge \bigwedge_\subbox{j \in J'_{13} \cap H'} \beta_{12j} = \beta_{13j} \nwedge g_{13} \wedge 
+			 R'\mpar{s'_{12}, s'_{13}}\psubst{\psi_{12} \uplus \psi_{13}}
 		\end{array}}   

### 2023-03-10 2021-Refinement/paper/refinementarticleV2.tex
lecture preuve

@@
   $t_{12}$ is obtained by the transition 
-$\OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{{(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1}$  alone with the state $s_2$ unchanged, if $k \not\in {J^1_{1}}^{\prime}$
+$t^1_1=\OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{{(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1}$  alone with the state $s_2$ unchanged, if $k \not\in {J^1_{1}}^{\prime}$
 \[t_{12} = \OT{\mpar{s^1_1, s_2}}{\mpar{{s^1_1}', s_2}}{\alpha_1^1}{ {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{g^1_1}{\psi^1_1}
@@
 
-Because the hole is not involved we can define (where elements of $A_1$ are the same as above modulo renaming of variables):
+Because the hole is not involved we can define $t_{13}$ with the same transition $t_1$ of $A_1$ (where elements of $t_1$ are the same as above modulo renaming of variables):
 \[t_{13} = \OT{\mpar{s^1_1, s_3}}{\mpar{{s^2_1}', s_3}}{\alpha_1^2}{ {(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{g^2_1}{\psi^2_1}
@@
 
+\RAB{Pourquoi masquer partie en dessous? we need to prove  $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$}
 % 
@@
 \[R' \mpar{s_{12}, s_{13}} =  R\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge s^1_1 = s^2_1 \]
-Thus, because transitions are the same:
+Thus, because transitions $t^1_1$ and  $t^2_1$ are the same:
 \[R' \mpar{s_{12}, s_{13}} \implies
-R\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge {s^1_1}^\prime = {s^2_1}^\prime
+\underbrace{R\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge {s^1_1}^\prime = {s^2_1}^\prime}_{R' \mpar{s'_{12}, s'_{13}}}
 \]
@@
 \[ \fvars{t_{12}} \vdash \left(\reach{A_{12}}\mpar{s_{12}} \wedge g_{12} \implies \reach{A_{12}}\mpar{s_{12}'}\psubst{\psi_{12}}\right) \]
+
+\RAB{Bien entendu ce passage est vrai que parce que  $\alpha_{12}$ and $\alpha_{13}$ are the same...}
 

### 2023-03-10 2021-Refinement/paper/refinementarticleV2.tex
lecture preuve thm3 - item 2 - second case

@@
 V_{13}= V^2_1\uplus V_3\\
-& H'=H\uplus J_1 \setminus \{k\} \subseteq J_1\uplus \mpar{J_2 \cap J_3} \setminus \{k\}= \mpar{J^1_1\uplus J_2 \setminus \{k\} } \cap \mpar{J^2_1\uplus J_3 \setminus \{k\}} \\ &\,\,\,\, = J_{12 } \cap J_{13}
+& H'=H\uplus J_1 \setminus \{k\} \subseteq J_1\uplus \mpar{J_2 \cap J_3} \setminus \{k\}= \mpar{J^1_1\uplus J_2 \setminus \{k\} } \cap \mpar{J^2_1\uplus J_3 \setminus \{k\}} \\ &\,\,\,\,\, = J_{12 } \cap J_{13}
 \end{align*}
@@
 
-Because the hole is not involved we can define $t_{13}$ with the same transition $t_1$ of $A_1$ (where elements of $t_1$ are the same as above modulo renaming of variables):
+\RAB{The composition of the family of OTs $t_{3x}^{x\in X}$ originating from $s_3$ which are related $s_2$ with the same transitions of $A_1$ (modulo renaming) as one used to build $t_{12}$ produces a single transition $t_{13}$.} This is,
+because the hole is not involved we can define $t_{13}$ with the same transition $t_1$ of $A_1$ (where elements of $t_1$ are the same as above modulo renaming of variables):
 \[t_{13} = \OT{\mpar{s^1_1, s_3}}{\mpar{{s^2_1}', s_3}}{\alpha_1^2}{ {(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{g^2_1}{\psi^2_1}
@@
 
-\RAB{Pourquoi masquer partie en dessous? we need to prove  $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$}
+\RAB{Pourquoi masquer partie en dessous dans le latex?\\ we need to prove  $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$}
 % 
@@
 
-\RAB{Bien entendu ce passage est vrai que parce que  $\alpha_{12}$ and $\alpha_{13}$ are the same...}
-
-From the above we can deduce the expected formula:
+\RAB{Because $\alpha_{12}$ and $\alpha_{13}$ are the same, as well as  $\beta_{12}$ and $\beta_{13}$ are the same (modulo renaming of variables), and by considering all the family of weak open transitions indexed over X starting from $s_{3}$ which are related with $s_{2}$, we deduce from the above the expected formula:}
+
+%From the above we can deduce the expected formula:
 \begin{multline*}

### 2023-03-16 2021-Refinement/paper/refinementarticleV2.tex
proof

@@
 
-\RAB{The composition of the family of OTs $t_{3x}^{x\in X}$ originating from $s_3$ which are related $s_2$ with the same transitions of $A_1$ (modulo renaming) as one used to build $t_{12}$ produces a single transition $t_{13}$.} This is,
-because the hole is not involved we can define $t_{13}$ with the same transition $t_1$ of $A_1$ (where elements of $t_1$ are the same as above modulo renaming of variables):
-\[t_{13} = \OT{\mpar{s^1_1, s_3}}{\mpar{{s^2_1}', s_3}}{\alpha_1^2}{ {(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{g^2_1}{\psi^2_1}
+The hole is not involved we can define $t_{13}$ with the same transition $t_1$ of $A_1$ (where elements of $t_1$ are the same as above modulo renaming of variables):
+\[t_{13} = \OT{\mpar{s^1_1, s_3}}{\mpar{{s^2_1}', s_3}}{\alpha_1^2}{ {(\beta^2_{1j})^{j \in {J^{2}_1}'} }}{g^2_1}{\psi^2_1}
 \]
-
-\RAB{Pourquoi masquer partie en dessous dans le latex?\\ we need to prove  $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$}
-% 
-%$\forall x \in X$ we have
-%\begin{align*}		
-%J'_{13x} \cap H' & =  J^{2 \prime}_1 \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \\
-%& =  J^{1 \prime}_1 \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \text{ since }  J^{2 \prime}_1 =  J^{1 \prime}_1\\
-%& = \mpar{J'_{12}\cap H' }
-%\end{align*}
-
-We have by definition 
+We thus take $({t_{13 x}})^{x\in X} = \{t_{13}\}$.
+$\forall x \in X$ we have $J'_{13x} =  {J^{2}_1}'$ and trivially:
+\begin{align*}		
+J'_{13x} \cap H' & =  J^{2 \prime}_1 \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \\
+& =  J^{1 \prime}_1 \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \text{ since }  J^{2 \prime}_1 =  J^{1 \prime}_1\\
+& = \mpar{J'_{12}\cap H' }
+\end{align*}
+
+Moreover, we have by definition 
 \[R' \mpar{s_{12}, s_{13}} =  R\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge s^1_1 = s^2_1 \]
@@
 
-\RAB{Because $\alpha_{12}$ and $\alpha_{13}$ are the same, as well as  $\beta_{12}$ and $\beta_{13}$ are the same (modulo renaming of variables), and by considering all the family of weak open transitions indexed over X starting from $s_{3}$ which are related with $s_{2}$, we deduce from the above the expected formula:}
-
-%From the above we can deduce the expected formula:
+Because $\alpha_{12}$ and $\alpha_{13}$ are the same, and also  $\beta_{12}$ and $\beta_{13}$ are the same (modulo renaming of variables), we deduce from the above the expected formula (instantiated with $X$ a singleton): %From the above we can deduce the expected formula:
 \begin{multline*}
@@
 R'\mpar{s_{12}, s_{13}} \wedge g_{12} 
-\implies \hspace{10em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
+\implies \hspace{10em}\\ %\operatorname*{\bigsymb{\bigvee}}_{x \in X}
+ \mpar{\everymath{\displaystyle}
+%\begin{array}{l}
 			\alpha_{12} = \alpha_{13} \wedge \bigwedge_\subbox{j \in J'_{13} \cap H'} \beta_{12j} = \beta_{13j} \nwedge g_{13} \wedge 
 			 R'\mpar{s'_{12}, s'_{13}}\psubst{\psi_{12} \uplus \psi_{13}}
-		\end{array}}   
+%		\end{array}
+}   
 \end{multline*}

### 2023-03-16 2021-Refinement/paper/refinementarticleV2.tex
reorganisation with new definitions

@@
 
-* case 2 of the proofs for both theorems
-
 * example
@@
 * global rewriting
+
+* choisir terminologie: refinement or simulation
 
@@
 Second we introduce a relation that relates two automata with different sets of holes, which allows us to take into account the open nature of open automata, and to deal with composition.
+Properties of the refinement are stated and proven on the second, more general version of the relation, they are thus also valid for the first simpler refinement relation.
 
@@
 We  then  define a refinement relation for open automata, first only considering two automata with the same set of holes in Section~\ref{sec:refinement} and generalize it to automata with a different set of holes in Section~\ref{sec:holes}.
-Section~\ref{sec:prop} is dedicated to formalize and prove basic properties of refinement in ; here we prove that refinement is a preorder and we focus on one composition property.
+Section~\ref{sec:prop} is dedicated to formalize and prove basic properties of refinement in ; here we prove that refinement is a preorder and has good composition property.
 In Section~\ref{sec:sota} we review related works, and Section~\ref{sec:ccl} concludes the paper.
@@
  \end{definition}
+Note in this definition, instead of matching an instantiated transition  of the first automata to another instantiated transition of the second, it matches an open transition $t_1$ to a family of covering open transitions $t_{2x}^{x\in X}$.
 Technically, the following sections do not rely on the definition of strong bisimulation on OA, but they follow the same principles and in particular the same way to faithfully simulate an open transition by a set of other open transitions.
-\begin{comment}
-\subsection{Reachability : check if useful?}
+Intuitively, this means that for every pair of related
+states $(s_1,s_2)$  of the two automata, and for every  transition of the first automaton from $s_1$, there is a set of matching transitions  of the second automaton  from $s_2$ such that the produced action match, the actions of the same holes and the successors are related after variable update.
+
+%\begin{comment}
+\subsection{Reachability}
+We finally define a predicate abstracting state reachability for open automata, it  allows us to reason on reachable states in an automaton.
+It can alternatively be seen as an abstraction of the reachable states under the form of a predicate that must stay verified along the execution of the open automaton.
 \begin{definition}[Reachability] \label{Def:Reach}
@@
 From an automation point of view, finding the most precise reachability predicate for a given automata is not decidable because of the symbolic nature of open automata, but only an over-approximation is necessary.
-An automatic tool would only need to find an over approximation of reachability to reason on composition that is compatible with deadlock reduction.
-We call \emph{non-blocking composition} a composition that can be safely be used to compose open automata that are involved in a deadlock reducing relation.
-
-\end{comment}
+
+%\end{comment}
 
@@
 Similarly to FH-bisimulation~\cite{fhbisim} we are interested  in finding relations between configurations of two open automata that contain variables and holes. 
-However here we want to build a refinement relation that  also guarantees that no deadlock is introduced when refining the automaton (at least not among the scenarios originally planned in the specification).
-The refinement relation should be conditioned by the internal states of the automata.
-More precisely, a refinement relation characterizes when two states are related, and this  characterisation is expressed as a predicate on the variables of the two automata.
-Thus, a refinement relation is a relation on OA configurations.
+We rely on a classical notion of simulation inspired from~\cite{fhbisim}.
+The idea is that two configurations related by a relation; if one state can do a transition, then the other can do a transition too.
+Like for bisimulation, refinement relation characterizes when two states are related, and this  characterisation is expressed as a predicate on the variables of the two automata.
+Refinement defines conditions on a predicate $R$ such that $R\mpar{s_1, s_2}$ is a predicate (possibly involving variables of the automata) that is true when the state $s_1$ of $A_1$ refines the state $s_2$ of $A_2$.
 
@@
 %The idea is that
-We rely on a classical notion of simulation inspired from~\cite{fhbisim}.
-The idea is that two configurations related by a relation; if one state can do a transition, then the other can do a transition too.
-But to limit the creation of deadlocks when simulating an automaton, we first define when a relation is preserved along identical transitions before characterising a first simple refinement relation  to compare automata with identical holes.
 
@@
 
-Let us first explain the reasons why simulation can introduce allow undesired behaviours to emerge and how we want to limit them. 
-The automaton that simulates a specification features any behaviour that contains the behaviour of the specification, or more precisely, for each state that simulates a state of the specification, the simulating automaton must at least feature the behaviour of the specification.
- In this definition, nothing prevents the implementation from adding non-determinism and non-deterministically reaching a state that is unrelated to the specification, this state could even be a deadlock even though we only followed transitions that exist in the specification.
-To avoid the appearance of such deadlocks, we will state that, when both the implementation and the specification do the same transition, they stay related.
-This ensures a form of continuity in the comparison in the sense that the refined system is constrained to follow the behaviour of the simulated system along a given scenario. 
-In terms of traces this amounts to some form of deadlock reduction: for each trace followed by the simulated system if the refined system followed the beginning of the trace, it must be able to keep following the trace.
-Of course, the classical trace view is a simplified view compared to the guards, states and actions from  the holes that exist in OA, but it gives the right intuition.
-
+However here we want to build a refinement relation that  also guarantees that no deadlock is introduced when refining the automaton, this property is quite frequent in refinement relation, and referred to as \emph{lack of new deadlocks}~\cite{Kouchnarenko:2007} or \emph{complete simulation}~\cite{sangiorgi:bisim-coind12}.
+The notion of deadlock should however be specialized to our open automata.
+Indeed, the possible transitions are better characterized by the guards of the outgoing transitions from a given state, rather than the simple existence of a transition.
+We thus define a deadlock reduction criteria based on how the outgoing transitions are guarded.
+As such, a refinement does not introduce deadlocks if in the conditions where no transition is possible in the refined automaton, no transition are already possible in the more general one.
+More formally, for any pair of states $s_1$ and $s_2$  we introduce a criteria of the form:
+\[
+\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \wedge \lnot( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )\implies \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
+\]
+
+Which can be rewritten as:
+\[
+\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
+\]
+
+Both statements being equivalent and one of them may reveal more intuitive than the other in different conditions, we will use them interchangeably.
+%Let us first explain the reasons why simulation can introduce allow undesired behaviours to emerge and how we want to limit them. 
+%The automaton that simulates a specification features any behaviour that contains the behaviour of the specification, or more precisely, for each state that simulates a state of the specification, the simulating automaton must at least feature the behaviour of the specification.
+% In this definition, nothing prevents the implementation from 
+%
+%adding non-determinism and non-deterministically reaching a state that is unrelated to the specification, this state could even be a deadlock even though we only followed transitions that exist in the specification.
+%To avoid the appearance of such deadlocks, we will state that, when both the implementation and the specification do the same transition, they stay related.
+%This ensures a form of continuity in the comparison in the sense that the refined system is constrained to follow the behaviour of the simulated system along a given scenario. 
+%In terms of traces this amounts to some form of deadlock reduction: for each trace followed by the simulated system if the refined system followed the beginning of the trace, it must be able to keep following the trace.
+%Of course, the classical trace view is a simplified view compared to the guards, states and actions from  the holes that exist in OA, but it gives the right intuition.
 %
@@
 This is very weak but sufficient when composed with the def  of simulation.
-
 %\begin{definition}[Preservation along identical transitions]\label{def:preservation} \\
@@
 %\end{definition}
-
-We thus define the following property that can be understood as follows.
+%We thus define the following property that can be understood as follows.
 Take a specification automaton and its implementation.
@@
 Suppose an identical transition exist in both automata (with same guards and same label), then either the reached states $s_1'$ and $s_2'$ are related by refinement, or there exists another transition of the specification that is also identical and leads to a state $s_1''$ that is related to $s_2'$ in the refinement relation.
-Finally, we should take into account that 1) instead of equality, we should check if there is a state such that both transitions are feasible (the conjunction of guards is satisfiable), and that  2) instead of finding another transition of the specification we might find a family of transitions that cover all the cases of the transition of the implementation.
-
-We define now a simulation between OA that have the same set of holes.
-This relation thus focuses on the simulation of transitions and uses the previous definition to prevent the refined automaton from non-deterministically reaching states that introduce deadlocks in a scenario planned without deadlock in the specification.
-
-\begin{definition}[Hole-equal simulation]
+%Finally, we should take into account that 1) instead of equality, we should check if there is a state such that both transitions are feasible (the conjunction of guards is satisfiable), and that  2) instead of finding another transition of the specification we might find a family of transitions that cover all the cases of the transition of the implementation.
+We can now state the definition of simulation between OAs that have the same set of holes.
+
+\begin{definition}[Hole-equal simulation]\label{def:HoleEqualSim}
 Consider two OA with identical set of holes:  \(\OAg[1]\) and \(\OAg[2]\) where  \(J_1 = J_2\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $S_1$ to $S_2$ if the following conditions hold (we could denote it $A_1\leq A_2$):
@@
 \end{multline*}
-\item [(3)] The deadlock reduction:
-\begin{multline*}
-\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \wedge \lnot( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )\implies \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
-\end{multline*}
-
-Which can be rewritten as:
-\begin{multline*}
+\item [(3)] Deadlock reduction:
+\[
 \forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
-\end{multline*}
+\]
 
@@
 
-Note in this definition, instead of matching an instantiated transition (with all variables assigned) of the first automata to another instantiated transition of the second, it matches an open transition $t_1$ to a family of covering open transitions $t_{2x}^{x\in X}$.
  %Note also the second part of the conjunction of condition (2) expresses the deadlock reduction between automata (as introduced in Definition \ref{def:dpwd}).   
@@
 The third condition ensures that the refinement relation prevents the introduction of deadlocks.
-
-Intuitively, this means that for every pair of related
-states $(s_1,s_2)$  of the two automata, and for every  transition of the first automaton from $s_1$, there is a set of matching transitions  of the second automaton  from $s_2$ such that the produced action match, the actions of the same holes and the successors are related after variable update.
-Our definition captures a simple kind of sub-classing of open automata with the same holes.
-It is stronger than a strict simulation since it matches a transition with a family of transitions.
-With such a relation we are able to check the refinement between two open automata with the same level of abstraction but specified differently, for example, by duplicating states, removing transitions,  reinforcing  guards, modifying variables.
-
-The principle of the third requirement is that the relation allows new behaviour to be added in terms of new traces, but doesn't allow new deadlocks to
-be added, i.e., for every ``path'' of the specification (abstract automaton) the implementation (refined automaton) must not add deadlocks.
-
-This definition leads to a notion of simulation as refinement similar to the one used in LOTOS \cite{Brinksma:87} and called ``extension refinement''.
-The extension consists in adding new functionalities by preserving existing ones.
-In the context of LOTOS, a functionality is roughly an acceptable trace.
-In this context, the authors define refusal of the trace and constraint refinement so that there is no more refused trace in the refined system than in the original one.
+Our definition captures a simple kind of sub-classing of open automata with the same holes. It is more expressive than a strict simulation since it matches a transition with a family of transitions. 
+With such a relation we are able to check the refinement between two open automata with the same level of abstraction but specified differently, for example, by duplicating states, removing transitions,  reinforcing  guards, modifying variables, etc.
+We will show in Section~\ref{sec:prop} that this refinement relation has good properties in terms of transitivity, compositionality, and reflexivity.
+
+%The principle of the third requirement is that the relation allows new behaviour to be added in terms of new traces, but doesn't allow new deadlocks to
+%be added, i.e., for every ``path'' of the specification (abstract automaton) the implementation (refined automaton) must not add deadlocks.
+
+%This definition leads to a notion of simulation as refinement similar to the one used in LOTOS \cite{Brinksma:87} and called ``extension refinement''.
+%The extension consists in adding new functionalities by preserving existing ones.
+%In the context of LOTOS, a functionality is roughly an acceptable trace.
+%In this context, the authors define refusal of the trace and constraint refinement so that there is no more refused trace in the refined system than in the original one.
 Slightly more formally, consider an automaton with transitions $s_0 \xrightarrowdbl{t}$, consider $\mathcal{T}_A$ the set of traces of an automaton $A$; one can define the refusal of a trace $t$ as a set of actions such that all actions in the set can be refused after the automaton $A$ has performed the steps in the trace $t$, more precisely $X$ is a refusal of a trace if $\exists s.
@@
 
-Considering an OA with no  hole and no guard, i.e., in case the definitions of open automata coincide with those of automata, the fact that $R$ is preserved along identical traces ensures that the set  of refusal of valid traces is smaller in the refined automaton than in the specification.
+%Considering an OA with no  hole and no guard, i.e., in case the definitions of open automata coincide with those of automata, the fact that $R$ is preserved along identical traces ensures that the set  of refusal of valid traces is smaller in the refined automaton than in the specification.
 
@@
 
-The refinement relation  also specifies that the refined process must follow the behaviour of the specification, not only at every compatible state but also along any scenario of the specification.
-We will show in Section~\ref{sec:prop} that this refinement relation has good properties in terms of transitivity, compositionality, and reflexivity.
+%The refinement relation  also specifies that the refined process must follow the behaviour of the specification, not only at every compatible state but also along any scenario of the specification.
 
@@
 More generally, it should be possible to relate automata that do not have the same holes because composition is a crucial part of system specification.
-Thus, we believe composition should also be a form of refinement and call this feature \emph{refinement through composition}.
+%Thus, we believe composition should also be a form of refinement and call this feature \emph{refinement through composition}.
 However, filling holes can result in a system with more or less holes than the original system because the plugged subsystem can contain itself many holes.
-Next section will define  a more powerful refinement relation able to reason on automata with different sets of holes.
+Next section  defines  a more powerful refinement relation able to reason on automata with different sets of holes.
 
@@
 This section  extends the preceding relation to automata where the set of holes is not the same.
-A simple use-case for this is filling a hole with a completely defined automaton.
-In this case, we want to ensure that the automaton with a filled hole is a refinement of the other automata: actions of the identical holes will be taken into account the same way.
-
-\TODO{La section 4.1 reintroduit la notion de reachability et non introduction de blocage}
+Indeed, when composing the set of  holes changes, and for example we want to state whether the automaton after composition is a refinement of the original automaton or not.
+
 \subsection{Deadlock Reduction, Reachability, and Composition}
 
-A notion that is often used in the context of refinement is the notion of deadlock reduction.
+%A notion that is often used in the context of refinement is the notion of deadlock reduction.
 This property considers that two states related by a given relation and states that if one state can do a transition, then the other can do a transition too.
@@
 However, when the relation that relates states is a simulation, this will relate the possible transitions and the deadlock reduction will become a valuable property.
+\begin{comment}
 
@@
 The alternative definition is equivalent to this one when reasoning on a refinement relation (but not in general).
-
-Unfortunately, this property is not compositional: the composition operator can itself introduce a deadlock.
+\end{comment}
+
+Unfortunately, the deadlock reduction property in the definition of refinement is not compositional: the composition operator can itself introduce a deadlock.
 In other words, when filling the hole of two related automata with a third one, even if there is a deadlock reduction between the two original automata, there might not be a deadlock reduction in the composed ones.
@@
 This creates a conflict between deadlock reduction and the properties involving composition. 
-One possible solution to avoid this conflict is to only consider a composition that do not introduce deadlocks, we will define such a composition below.
-But before defining non-blocking composition, we first introduce a notion of state reachability for open automata. 
-\begin{definition}[Reachability] \label{Def:Reach}
-For any open automata \(A = \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is any predicate on states that is valid on initial state, and preserved across transitions:
-\[\sigma_0 \vdash \reach{A}\mpar{s_0}\quad\land\quad\forall t = \OTg \in T, \fvars{t} \vdash \left(\reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}\right)\]
-\end{definition}
-Reachability takes into account all paths, and can over-approximate the reachable configurations. 
-From an automation point of view, finding the most precise reachability predicate for a given automata is not decidable because of the symbolic nature of open automata, but only an over-approximation is necessary.
+%One possible solution to avoid this conflict is to only consider a composition that do not introduce deadlocks, we  define such a composition below.
+%But before defining non-blocking composition, we first introduce a notion of state reachability for open automata. 
+%\begin{definition}[Reachability] \label{Def:Reach}
+%For any open automata \(A = \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is any predicate on states that is valid on initial state, and preserved across transitions:
+%\[\sigma_0 \vdash \reach{A}\mpar{s_0}\quad\land\quad\forall t = \OTg \in T, \fvars{t} \vdash \left(\reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}\right)\]
+%\end{definition}
+%Reachability takes into account all paths, and can over-approximate the reachable configurations. 
+%From an automation point of view, finding the most precise reachability predicate for a given automata is not decidable because of the symbolic nature of open automata, but only an over-approximation is necessary.
 An automatic tool would only need to find an over approximation of reachability to reason on composition that is compatible with deadlock reduction.
@@
 \end{definition}
-Again we use guards to ensure that the transition can occur. It is not sufficient to ensure the existence of equivalent transitions in general, but it will be sufficient in the context of refinement.
+Like in the definition of refinement (Definition~\ref{def:HoleEqualSim}) we use guards to ensure that the transition can occur. 
+In general, one would not want to only consider non-blocking composition as it may reveal a bit restrictive, but it is the best necessary condition that can be identified for compositionality of refinement.
+It will be used to prove composition theorems in  Section~\ref{sec:prop}.
+Proving refinement relation in absence of non-blocking composition can always be done specifically for the composed automaton under study.
+%It is not sufficient to ensure the existence of equivalent transitions in general, but it will be sufficient in the context of refinement.
 
@@
 
-The major challenge in the design of this relation is to maintain a form of transitivity while being able to take into account the actions of some of the holes.
-A naive definition of refinement would ensure that the holes that are identical in the two open automata are taken into account in the simulation.
+One major challenge in the extension of refinement to different sets of holes is to maintain a form of transitivity while being able to take into account the actions of some of the holes.
+A naive definition of refinement would ensure that only the holes that are identical in the two open automata are taken into account in the simulation.
 Unfortunately considering all the common holes does not ensure transitivity of the simulation for the following reason.
@@
 \end{multline*}
-\item[(3)] $R$ is preserved along identical transitions of \(A_1\) and \(A_2\).
-
-Giving \(R\) and \(H\) is sufficient to characterise the refinement, so we call \(\mpar{R, H}\) a hole-tracking simulation of \(A_1\) by \(A_2\).
-Hole in \(H\) are called tracked holes.
+\item[(3)] Deadlock reduction:
+\[
+\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
+\]
 \end{definition}

### 2023-03-17 2021-Refinement/paper/refinementarticleV2.tex
proof sketch and properties section

@@
 \end{definition}
-Note that every action of the holes outside \(H\) is unconstrained in the related automata.
+Note that every action of the holes outside \(H\) is unconstrained according to the refinement relation.
 
@@
 We now  state the properties of our refinement relations, proofs of the properties can be found in the appendices.
-We express these properties in terms of open automata refinement because hole-equal simulation is a particular case of Definition~\ref{Def:OA-Refinement} when  $J_1=J_2=H$, and thus most of the properties shown here are easy to adapt to hole-equal simulation.
-
+We express these properties in terms of open automata refinement because hole-equal simulation is a particular case of Definition~\ref{Def:OA-Refinement} when  $J_1=J_2=H$, and thus all the properties shown here are trivially true for hole-equal simulation.
 The first crucial property of  refinement  is that it is  a  preorder on the set of open automata. This property enables stepwise refinement.
@@
 
+\begin{proofsketch}
 % TODO: I don't understand this definition, why v = v on vars(s1), what about s2
@@
 We then prove that this relation  is a refinement, according to Definition~\ref{Def:OA-Refinement}.
+
+\end{proofsketch}
 

### 2023-03-22 2021-Refinement/paper/refinementarticleV2.tex
NB composition

@@
 
+%\begin{definition}[Non-blocking composition] \label{Def:Non-block}
+%Let \(A_i = \OAg[i]\) with \( 0 \leq i \leq n\) be a family of open automata.
+%Let \(A = A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) and $A= \OAg$.
+%
+%The composition \(A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is non-blocking if   \(A \) has a reachability predicate such that, for each reachable configuration, if there is a possible transition in \(A_0\) then there is a possible transition in \(A\):
+%\begin{multline*}
+% \forall s = \mpar{s_0, s_1,..,s_n} \in S, V \uplus \biguplus_\subbox{t_0 \in \fOT{s_0}} \fvars{t_0} \vdash \\ \left(\reach{A}\mpar{s} \wedge \bigvee_\subbox{t_0 \in \fOT{s_0}} \fguard{t_0} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \right)
+%\end{multline*}
+%\end{definition}
 \begin{definition}[Non-blocking composition] \label{Def:Non-block}
-Let \(A_i = \OAg[i]\) with \( 0 \leq i \leq n\) be a family of open automata.
-Let \(A = A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) and $A= \OAg$.
-
-The composition \(A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is non-blocking if   \(A \) has a reachability predicate such that, for each reachable configuration, if there is a possible transition in \(A_0\) then there is a possible transition in \(A\):
-\[ \forall s = \mpar{s_0, s_1,..,s_n} \in S, V \uplus \biguplus_\subbox{t_0 \in \fOT{s_0}} \fvars{t_0} \vdash \left(\reach{A}\mpar{s} \wedge \bigvee_\subbox{t_0 \in \fOT{s_0}} \fguard{t_0} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \right)\]
+Let \(A_1 \defobject \OAg[1]\), \( A_2 \defobject \OAg[1]\) be two open automata.
+Let \(A = A_1\subst{A_2}{k}\) and $A= \OAg$.
+
+The composition \(A_1\subst{A_2}{k}\) is non-blocking if   \(A \) has a reachability predicate such that, for each reachable configuration, if there is a possible transition in \(A_1\) then there is a possible transition in \(A\):
+\begin{multline*}
+ \forall s = \mpar{s_1, s_2} \in S, V \uplus \biguplus_\subbox{t \in \fOT{s_1}} \fvars{t} \vdash \\ \left(\reach{A}\mpar{s} \wedge \bigvee_\subbox{t \in \fOT{s_1}} \fguard{t} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \right)
+\end{multline*}
 \end{definition}

### 2023-04-03 2021-Refinement/paper/refinementarticleV2.tex
add figures FIFO
add figures...
minor todo
ajout figures dans le tex
trvail sur les figures

@@
 
-\begin{example} As a running example, we consider a data base example inspired from \cite{Gorrieri:2001}.
+\TODO{Debut Exemple-1}
+\begin{example} As a running example, we consider a classical producer-consumer pair  with FIFO buffer. The overall structure shown in Fig. \ref{Fig:Architect}
+reflects the different processes involved in the communication and all the actions performed.
+
+\begin{figure}[h]
+ \centering
+   \includegraphics[width=.70\textwidth]{Figures/Architecture.pdf}
+   \caption{Open Automaton. It exposes an unspecified counter in the "cnt" hole
+ to count external tick actions.
+The system sets a counter when a query is enabled and updates  when  the time is over.\label{Fig:Architect}} \TODO{refaire l exemple pour l instant il a pas vraiment de sens}
+\end{figure}
+
+The open automaton  modelling the behaviour of the \texttt{prod-cons}  system is depicted in Fig.
+\ref{Fig:SpecOA}.
+The \texttt{prod-cons} can be fed using an operation \texttt{push} and discharged  using an operation \texttt{pop}.
+The automata has two holes: $\texttt{P}$ and  $\texttt{Q}$  depicting  the behaviour of the producer and consumer resp.
+When the \texttt{prod-cons} agrees with $\texttt{P}$ on a data admission, it   stores the data in a local variable and  exposes to the environment an observable action \texttt{push}.
+At the opposite side, when it agrees with $\texttt{Q}$ on a data retrieval, it exposes  a \texttt{pop} action.
+It can also agree with $\texttt{Q}$ on admission of data but this one is rather printed not stored (\texttt{pop(m)}).
+Besides, producing and  consuming, it can agree on the computation action of both processes but this action is exposed as unobservable actions $\tau$.
+
+\medskip
+
+a data base example inspired from \cite{Gorrieri:2001}.
 The open automaton \texttt{database}  modelling the behaviour of data base is depicted in Fig.
@@
  \centering
-   \includegraphics[width=.9\textwidth]{Figures/database.pdf}
+   \includegraphics[width=.95\textwidth]{Figures/FIFOpen2.pdf}
    \caption{Open Automaton. It exposes an unspecified counter in the "cnt" hole
@@
  \centering
-   \includegraphics[width=.55\textwidth]{Figures/counter.pdf}\hfill 
-   \includegraphics[width=.35\textwidth]{Figures/compose_count_db.pdf}
+   \includegraphics[width=.35\textwidth]{Figures/P-proc.pdf}\hfill 
+   \includegraphics[width=.45\textwidth]{Figures/Q-proc.pdf}
    \caption{(Left) Open Automaton of \texttt{counter} process.
@@
 
+\TODO{parler de generalisation a la composition a n automates}
+
 \section{Related Work}
@@
 
+\newpage
+
+\section{Example}
+\TODO{A completer...}
+
+\begin{figure}[!tb]
+ \centering
+   \includegraphics[width=.65\textwidth]{Figures/Architecture.pdf}
+   \caption{\texttt{Archtecture du systeme}. \label{Fig:Archi}}
+\end{figure}
+
+\begin{figure}[!tb]
+ \centering
+   \includegraphics[width=.90\textwidth]{Figures/FIFOpen2.pdf}
+   \caption{\texttt{FIFO} process.
+Two other actions,  in addition to  \texttt{p-a} and \texttt{p-b},  \texttt{in} representing a     \texttt{out} are used to reflect the actual operation of copying.
+\label{Fig:FIFOA}}
+\end{figure}
+
 %\section{Proof of Transitivity for Refinement}\label{sec:proof-transitivity}
 
+\begin{figure}[!tb]
+ \centering
+   \includegraphics[width=1.25\textwidth]{Figures/FIFORing.pdf}
+   \caption{\texttt{FIFO} process.  \label{Fig:RefineOA}}
+\end{figure}
+
+\begin{figure}[h]
+ \centering
+   \includegraphics[width=.40\textwidth]{Figures/P-proc.pdf}\hfill 
+   \includegraphics[width=.55\textwidth]{Figures/Q-proc.pdf}
+   \caption{(Left) Open Automaton of \texttt{P} process.   (Right) Open Automaton of  \texttt{Q} process.\label{Fig:processes}}
+\end{figure}
+
 \end{document}

### 2023-04-04 2021-Refinement/paper/refinementarticleV2.tex
add Figures

@@
 \TODO{Debut Exemple-1}
-\begin{example} As a running example, we consider a classical producer-consumer pair  with FIFO buffer. The overall structure shown in Fig. \ref{Fig:Architect}
-reflects the different processes involved in the communication and all the actions performed.
+\newpage
+\begin{example} As a running example, we consider a classical producer-consumer pair  with FIFO buffer,  referred to as \texttt{prod-cons}.
+The  structure shown in Fig.
+\ref{Fig:Architect} reflects the different processes involved in the system and all the actions performed.
 
@@
    \includegraphics[width=.70\textwidth]{Figures/Architecture.pdf}
-   \caption{Open Automaton. It exposes an unspecified counter in the "cnt" hole
- to count external tick actions.
-The system sets a counter when a query is enabled and updates  when  the time is over.\label{Fig:Architect}} \TODO{refaire l exemple pour l instant il a pas vraiment de sens}
+   \caption{The structure of the example \label{Fig:Architect}} 
 \end{figure}
@@
 At the opposite side, when it agrees with $\texttt{Q}$ on a data retrieval, it exposes  a \texttt{pop} action.
-It can also agree with $\texttt{Q}$ on admission of data but this one is rather printed not stored (\texttt{pop(m)}).
+The system can also agree with $\texttt{Q}$ on the admission of data but this one is rather printed not stored.
 Besides, producing and  consuming, it can agree on the computation action of both processes but this action is exposed as unobservable actions $\tau$.
 
-\medskip
-
-a data base example inspired from \cite{Gorrieri:2001}.
-The open automaton \texttt{database}  modelling the behaviour of data base is depicted in Fig.
-\ref{Fig:SpecOA}.
-The \texttt{database} can be queried using an operation \texttt{qry} and updated using an operation \texttt{upd}.
-The associated automaton has a single hole:  a counter ($\texttt{cnt}$)  depicting  the behaviour of the timer.
-When the \texttt{database}  performs a query,  it sets the new time limit of the counter component and the exposed action to the environment is an observable  action \texttt{qry}.
-The \texttt{database} updates and  switches when it agrees with the counter component the time is over, and the exposed action is \texttt{upd}.
-The open automaton \texttt{counter}    depicting  the behaviour of the timer is illustrated in Fig. \ref{Fig:counter}. 
-\end{example}
 \begin{figure}[h]
@@
    \includegraphics[width=.95\textwidth]{Figures/FIFOpen2.pdf}
-   \caption{Open Automaton. It exposes an unspecified counter in the "cnt" hole
- to count external tick actions.
-The system sets a counter when a query is enabled and updates  when  the time is over.\label{Fig:SpecOA}} \TODO{refaire l exemple pour l instant il a pas vraiment de sens}
+   \caption{Open Automaton of the \texttt{prod-cons} system. It exposes two unspecified processes in holes
+   $\texttt{P}$ and  $\texttt{Q}$. \label{Fig:SpecOA}} \TODO{refaire l exemple pour l instant il a pas vraiment de sens}
 \end{figure}
+
+\end{example}
 
@@
 The plugging operation is called composition.
-The composition of OA was already implicitly defined by the means of composition on pNets in previous work \cite{henrio:01299562} but never  formalised on OA\footnote{The definition of composition below is a direct translation of what happens with pNets composition \cite{henrio:01299562} without  introducing pNets.}
+The composition of OA was already implicitly defined by the means of composition on pNets in previous work \cite{henrio:01299562} but never  formalised on OA.\footnote{The definition of composition below is a direct translation of what happens with pNets composition \cite{henrio:01299562} without  introducing pNets.}
 
@@
 
-The first OA decides when the second can evolve by involving its hole in a transition:
-the action emitted when \(A_p\) makes a transition is synchronised with the action of the hole \(k\) in transitions of \(A_c\).
-
+The first OA decides when the second can evolve by involving its hole in a transition: the action emitted when \(A_p\) makes a transition is synchronised with the action of the hole \(k\) in transitions of \(A_c\).
+
+\begin{example}
+
+Two processes that are composable with the open automaton in  Fig. \ref{Fig:SpecOA} are those given in  Fig. \ref{Fig:procandcons}. 
 \begin{figure}[h]
@@
    \includegraphics[width=.45\textwidth]{Figures/Q-proc.pdf}
-   \caption{(Left) Open Automaton of \texttt{counter} process.
-Its role is to get a target, then count ticks until that target is reached, then emits an action with the elapsed time and restart.
-(Right) Open Automaton of the composition \texttt{database}[\texttt{counter/cnt}].\label{Fig:counter}}
+   \caption{(Left) Open Automaton of the \texttt{producer}.
+It  transmits data calculated, sending one item at a time to the FIFO.
+(Right) The \texttt{consumer} gets one item at a time from the FIFO and sends it after a prior processing.
+\label{Fig:procandcons}}
 \end{figure}
-
-\begin{example}
-In Fig.
-\ref{Fig:counter} (right) we present the composition \texttt{database}[\texttt{counter/cnt}] of the two open automata \texttt{database} and \texttt{counter}.
-Each state of the composite consists of a state of \texttt{database} together with a state of \texttt{counter}.
-The composed automaton  takes over  the same steps as the   \texttt{database} automaton but it also includes new steps,  indicating the change of states for the setting of timer.
-Note how restricting the composition to a synchronisation of actions (of the encompassing automaton and  of the hole) corresponds to imposing of a change in states.
-This example also shows how value passing works: the time limit of the counter is set by the parameter \texttt{n} carried by  the \texttt{set} action.
+~~\\
+\smallskip
+\RAB{Pbme: L'automate de la fig \ref{Fig:ComposeOA} n'est pas le resultat de la composition du prod et cons avec la sepc, i.e l'automate de la fifure \ref{Fig:SpecOA} mais avec celui du raffine (qui vient apres) i.e fig \ref{Fig:RefineOA}.
+Solutions: 1) deplacer la composition 2) refaire la figure l'automate sera un peu plus gros?
+}
+\begin{figure}[h]
+ \centering
+   \includegraphics[width=.95\textwidth]{Figures/compos-FIFO-Pro.pdf}
+   \caption{Open Automaton of the \texttt{prod-cons}[\texttt{P}/\texttt{producer}]. 
+   $\texttt{P}$ and  $\texttt{Q}$. \label{Fig:ComposeOA}} 
+\end{figure}
 \end{example}
@@
   \end{minipage}
-$s$ and $t$ are bisimilar, written $s\tilde t$ iff there is a bisimulation relation $R$ sucht that  $s ~\mathcal{R}~ t$
+$s$ and $t$ are bisimilar, written $s\sim t$ iff there is a bisimulation relation $R$ such that  $s ~\mathcal{R}~ t$
 \end{definition}
@@
 \begin{example} 
-To illustrate the refinement simulation of open automata, consider a variation on the \texttt{database}.
-We suppose that on more concrete level, in addition to querying and updating the data base,  a backup copy of it may also be made.
+To illustrate the refinement simulation of open automata, consider a variation on the \texttt{prod-cons}.  We suppose that on more concrete level,
+FIFO circular buffer
   The behaviour of the concrete database is given by 
@@
  \centering
-   \includegraphics[width=.9\textwidth]{Figures/databaseRefine.pdf}
-   \caption{Another variant of the \texttt{database} process.
-Two other actions,  in addition to  \texttt{qry} and \texttt{upd},  \texttt{back} representing a request to make a backup copy and    \texttt{cpy} are used to reflect the actual operation of copying.
-\label{Fig:RefineOA}}
+   \includegraphics[width=.99\textwidth]{Figures/FIFORing.pdf}
+   \caption{Open Automation of the \texttt{prod-cons} system communicating through a FIFO circular buffer.  \label{Fig:RefineOA}}
 \end{figure}
@@
 
-\begin{figure}[h]
- \centering
-   \includegraphics[width=.6\textwidth]{Figures/composeRefined.pdf}
-   \caption{Open automata resulting from the composition of the  refined  \texttt{database} and the \texttt{counter} \label{Fig:ComposeRefine}}
-\end{figure}
+%\begin{figure}[h]
+% \centering
+%   \includegraphics[width=.6\textwidth]{Figures/composeRefined.pdf}
+%   \caption{Open automata resulting from the composition of the  refined  \texttt{database} and the \texttt{counter} \label{Fig:ComposeRefine}}
+%\end{figure}
 
@@
 
-\newpage
-
-\section{Example}
-\TODO{A completer...}
-
-\begin{figure}[!tb]
- \centering
-   \includegraphics[width=.65\textwidth]{Figures/Architecture.pdf}
-   \caption{\texttt{Archtecture du systeme}. \label{Fig:Archi}}
-\end{figure}
-
-\begin{figure}[!tb]
- \centering
-   \includegraphics[width=.90\textwidth]{Figures/FIFOpen2.pdf}
-   \caption{\texttt{FIFO} process.
-Two other actions,  in addition to  \texttt{p-a} and \texttt{p-b},  \texttt{in} representing a     \texttt{out} are used to reflect the actual operation of copying.
-\label{Fig:FIFOA}}
-\end{figure}
-
-%\section{Proof of Transitivity for Refinement}\label{sec:proof-transitivity}
-
-\begin{figure}[!tb]
- \centering
-   \includegraphics[width=1.25\textwidth]{Figures/FIFORing.pdf}
-   \caption{\texttt{FIFO} process.  \label{Fig:RefineOA}}
-\end{figure}
-
-\begin{figure}[h]
- \centering
-   \includegraphics[width=.40\textwidth]{Figures/P-proc.pdf}\hfill 
-   \includegraphics[width=.55\textwidth]{Figures/Q-proc.pdf}
-   \caption{(Left) Open Automaton of \texttt{P} process.   (Right) Open Automaton of  \texttt{Q} process.\label{Fig:processes}}
-\end{figure}
-
 \end{document}

### 2023-04-07 2021-Refinement/paper/refinementarticleV2.tex
work on the example

@@
 \newpage
-\begin{example} As a running example, we consider a classical producer-consumer pair  with FIFO buffer,  referred to as \texttt{prod-cons}.
-The  structure shown in Fig.
-\ref{Fig:Architect} reflects the different processes involved in the system and all the actions performed.
+\begin{example} As a running example, we consider a classical producer-consumer pair  interacting through FIFO buffer,  referred to as \texttt{prod-cons}.
+Fig.
+\ref{Fig:Architect} reflects the overall structure of the system involving a producer process, a consumer process and an orchestrator that coordinates  their activities.
 
@@
    \includegraphics[width=.70\textwidth]{Figures/Architecture.pdf}
-   \caption{The structure of the example \label{Fig:Architect}} 
+   \caption{Structure of the example.
+Each box corresponds to a process whose ports are the actions it can perform.
+The  actions observable by the environment are $\texttt{push}$, which indicates the enqueuing of an element, $\texttt{pop}$ which indicates the dequeuing, and $\texttt{print}$ which indicates the outing of results.
+\label{Fig:Architect}}
 \end{figure}
 
-The open automaton  modelling the behaviour of the \texttt{prod-cons}  system is depicted in Fig.
-\ref{Fig:SpecOA}.
-The \texttt{prod-cons} can be fed using an operation \texttt{push} and discharged  using an operation \texttt{pop}.
-The automata has two holes: $\texttt{P}$ and  $\texttt{Q}$  depicting  the behaviour of the producer and consumer resp.
-When the \texttt{prod-cons} agrees with $\texttt{P}$ on a data admission, it   stores the data in a local variable and  exposes to the environment an observable action \texttt{push}.
-At the opposite side, when it agrees with $\texttt{Q}$ on a data retrieval, it exposes  a \texttt{pop} action.
-The system can also agree with $\texttt{Q}$ on the admission of data but this one is rather printed not stored.
-Besides, producing and  consuming, it can agree on the computation action of both processes but this action is exposed as unobservable actions $\tau$.
-
+The open automaton  modelling the behaviour of such a system  using an  unbounded circular/ring buffer is depicted in Fig.
+\ref{Fig:RefineOA}.
+The automaton has a single state with  two holes: $\texttt{P}$ and  $\texttt{Q}$ reflecting the processes to manage the producer and consumer respectively.
+The two pointers $\texttt{l}$ and $\texttt{f}$  indicate resp.
+the next available position for  enqueuing an element  and the position that contains the next element to be dequeued %\footnote{The  arrow  without any state of origin is a graphical convention to indicate that the pointers are initialized at the beginning}.
+Whenever the buffer agrees with $\texttt{P}$ on the acquisition of an element, it enqueues it.
+Similarly, whenever it agrees with $\texttt{Q}$ on the retrieval, it dequeues an element.
+However, whenever $\texttt{Q}$ produces an item, it is exposed as an external observable  $\texttt{print}$ action.
+Whereas, when both processes do their internal computation, it is exposed externally as unobservable action $\tau$.
 \begin{figure}[h]
  \centering
-   \includegraphics[width=.95\textwidth]{Figures/FIFOpen2.pdf}
-   \caption{Open Automaton of the \texttt{prod-cons} system. It exposes two unspecified processes in holes
-   $\texttt{P}$ and  $\texttt{Q}$. \label{Fig:SpecOA}} \TODO{refaire l exemple pour l instant il a pas vraiment de sens}
+   \includegraphics[width=.99\textwidth]{Figures/FIFORing.pdf}
+   \caption{Open Automaton for the \texttt{prod-cons} system using FIFO circular buffer.
+    \label{Fig:RefineOA}} 
 \end{figure}
@@
 \end{example}
+
+\medskip
+\TODO{Fin Example-1}
 
@@
 
-\begin{example}
-
-Two processes that are composable with the open automaton in  Fig. \ref{Fig:SpecOA} are those given in  Fig. \ref{Fig:procandcons}. 
+\TODO{Debut -- Exemple 2}
+
+\begin{example} Examples of processes that can fill the holes of the considered automaton can also modelled by open automata as shown is  Fig. \ref{Fig:procandcons}.
  \begin{figure}[h]
@@
    \includegraphics[width=.45\textwidth]{Figures/Q-proc.pdf}
-   \caption{(Left) Open Automaton of the \texttt{producer}.
-It  transmits data calculated, sending one item at a time to the FIFO.
-(Right) The \texttt{consumer} gets one item at a time from the FIFO and sends it after a prior processing.
+   \caption{(Left) An example of a \texttt{producer}.
+It produces one item at a time and puts it to the buffer.
+(Right)  An example of a \texttt{consumer}.
+It gets an item from the buffer, does its work and returns the result.
 \label{Fig:procandcons}}
 \end{figure}
-~~\\
-\smallskip
-\RAB{Pbme: L'automate de la fig \ref{Fig:ComposeOA} n'est pas le resultat de la composition du prod et cons avec la sepc, i.e l'automate de la fifure \ref{Fig:SpecOA} mais avec celui du raffine (qui vient apres) i.e fig \ref{Fig:RefineOA}.
-Solutions: 1) deplacer la composition 2) refaire la figure l'automate sera un peu plus gros?
-}
+
+The open automaton on Fig.
+\ref{Fig:ComposeOA} is the composition of the specification on Fig.
+\ref{Fig:RefineOA} and the producer on Fig.
+\ref{Fig:procandcons}.
+The composition produces two states (le product of the states of both automata), the transitions from one state to another come from  the synchronisation  of the transitions of the encompassing automaton including the hole \texttt{P} and those of the producer filling the hole.
+Transitions involving \texttt{Q} remain unchanged.
+
 \begin{figure}[h]
  \centering
-   \includegraphics[width=.95\textwidth]{Figures/compos-FIFO-Pro.pdf}
+   \includegraphics[width=.99\textwidth]{Figures/compos-FIFO-Pro.pdf}
    \caption{Open Automaton of the \texttt{prod-cons}[\texttt{P}/\texttt{producer}]. 
-   $\texttt{P}$ and  $\texttt{Q}$. \label{Fig:ComposeOA}} 
+   \label{Fig:ComposeOA}} 
 \end{figure}
 \end{example}
+
+\TODO{Fin -- Exemple 2}
 
@@
 
+\TODO{Debut -- Example 3}
 \begin{example} 
-To illustrate the refinement simulation of open automata, consider a variation on the \texttt{prod-cons}.  We suppose that on more concrete level,
-FIFO circular buffer
-  The behaviour of the concrete database is given by 
-an open automaton  depicted in Fig. \ref{Fig:RefineOA}. 
+To illustrate the refinement simulation of open automata, consider a variation on the \texttt{prod-cons}.
+We suppose that  the two processes  \texttt{P} and  \texttt{Q} communicate through a one-place  buffer.
+The  corresponding behaviour  is given by  an open automaton  depicted in Fig.
+\ref{Fig:SpecOA}.
+\begin{figure}[h]
+ \centering
+   \includegraphics[width=.90\textwidth]{Figures/FIFOpen2.pdf}
+   \caption{Open Automation of the \texttt{prod-cons} system using one-place  buffer.  \label{Fig:SpecOA}}
+\end{figure}
+We can easily check that the automata on Fig.\ref{Fig:RefineOA} is a refinement of this automaton. $R=\{(r_0,s_0) \mapsto True, (r_0,s_1) \mapsto True \}$ is a simulation.
 \end{example}
-\begin{figure}[!tb]
- \centering
-   \includegraphics[width=.99\textwidth]{Figures/FIFORing.pdf}
-   \caption{Open Automation of the \texttt{prod-cons} system communicating through a FIFO circular buffer.  \label{Fig:RefineOA}}
-\end{figure}
+\TODO{Fin}
 

### 2023-04-13 2021-Refinement/paper/refinementarticleV2.tex
Examples

@@
 
-* example
+* example a terminer
 
@@
 
-* global rewriting
+* global rewriting (partly done)
 
@@
 
-\TODO{Debut Exemple-1}
-\newpage
-\begin{example} As a running example, we consider a classical producer-consumer pair  interacting through FIFO buffer,  referred to as \texttt{prod-cons}.
+\begin{example}[\texttt{prod-cons}]\label{ex:fifo-system} As a running example, we consider a classical producer-consumer pair  interacting through FIFO buffer,  referred to as \texttt{prod-cons}.
 Fig.
@@
 
-\begin{figure}[h]
+\begin{figure}[!ht]
  \centering
@@
 Each box corresponds to a process whose ports are the actions it can perform.
-The  actions observable by the environment are $\texttt{push}$, which indicates the enqueuing of an element, $\texttt{pop}$ which indicates the dequeuing, and $\texttt{print}$ which indicates the outing of results.
+The  actions observable by the environment are $\texttt{push}$, which indicates the enqueuing of an element, $\texttt{pop}$ which indicates the dequeuing, and $\texttt{print}$ which indicates the production of results.
 \label{Fig:Architect}}
@@
 
+The example uses several kinds of data.
+Variable $m$ holds a message, message types do not need a concrete definition here.
+We additionally use arrays of messages with a syntax of the form $M[l]$ for array accesses; $M$ is an array of $N$ elements, from $0$ to $N-1$.
+Finally we use addition and modulo operation ($\%$) on integers.
+
 The open automaton  modelling the behaviour of such a system  using an  unbounded circular/ring buffer is depicted in Fig.
 \ref{Fig:RefineOA}.
-The automaton has a single state with  two holes: $\texttt{P}$ and  $\texttt{Q}$ reflecting the processes to manage the producer and consumer respectively.
-The two pointers $\texttt{l}$ and $\texttt{f}$  indicate resp.
-the next available position for  enqueuing an element  and the position that contains the next element to be dequeued %\footnote{The  arrow  without any state of origin is a graphical convention to indicate that the pointers are initialized at the beginning}.
-Whenever the buffer agrees with $\texttt{P}$ on the acquisition of an element, it enqueues it.
-Similarly, whenever it agrees with $\texttt{Q}$ on the retrieval, it dequeues an element.
-However, whenever $\texttt{Q}$ produces an item, it is exposed as an external observable  $\texttt{print}$ action.
-Whereas, when both processes do their internal computation, it is exposed externally as unobservable action $\tau$.
-\begin{figure}[h]
+The automaton has a single state with  two holes: $\texttt{P}$ and  $\texttt{Q}$ that are the two interacting processes.
+$\texttt{l}$   indicates the next available position for  enqueuing an element  and  $\texttt{f}$ is the position that contains the next element to be dequeued.
+%\footnote{The  arrow  without any state of origin is a graphical convention to indicate that the pointers are initialized at the beginning}.
+The buffer reacts to a push from $\texttt{P}$ and enqueues it.
+Similarly, whenever it  $\texttt{Q}$ pops an element, it dequeues it.
+Additionally, whenever $\texttt{Q}$ produces an item, it is exposed as an external observable  $\texttt{print}$ action.
+When any process do its internal computation, it is exposed externally as unobservable action $\tau$. 
+\begin{figure}[!tb]
  \centering
@@
 \end{figure}
-
+\qed
 \end{example}
-
-\medskip
-\TODO{Fin Example-1}
 
@@
 
-\TODO{Debut -- Exemple 2}
-
-\begin{example} Examples of processes that can fill the holes of the considered automaton can also modelled by open automata as shown is  Fig. \ref{Fig:procandcons}.
- \begin{figure}[h]
+\begin{example} 
+ Fig. \ref{Fig:procandcons} shows a producer automaton  and a consumer  automaton that can be used  to fill the holes $P$ and $Q$ of \texttt{prod-cons} defined in Example~\ref{ex:fifo-system}.
+ \begin{figure}[!ht]
  \centering
@@
    \includegraphics[width=.45\textwidth]{Figures/Q-proc.pdf}
-   \caption{(Left) An example of a \texttt{producer}.
-It produces one item at a time and puts it to the buffer.
-(Right)  An example of a \texttt{consumer}.
-It gets an item from the buffer, does its work and returns the result.
-\label{Fig:procandcons}}
+   \caption{(Left) A \texttt{producer}.  It produces one item at a time and pushes it.  (Right)  A \texttt{consumer}. It pops an item, does some work and pushes the result. \label{Fig:procandcons}}
 \end{figure}
@@
 The open automaton on Fig.
-\ref{Fig:ComposeOA} is the composition of the specification on Fig.
-\ref{Fig:RefineOA} and the producer on Fig.
+\ref{Fig:ComposeOA} is the composition of the system in Fig.~\ref{Fig:RefineOA} and the producer in Fig.
 \ref{Fig:procandcons}.
-The composition produces two states (le product of the states of both automata), the transitions from one state to another come from  the synchronisation  of the transitions of the encompassing automaton including the hole \texttt{P} and those of the producer filling the hole.
+The composition consists of two states (the product of the states of both automata).
+The transitions from one state to another come from  the synchronisation  of the transitions of the encompassing automaton with those of the producer filling the hole $P$.
 Transitions involving \texttt{Q} remain unchanged.
-
-\begin{figure}[h]
+\qed
+
+\begin{figure}[!ht]
  \centering
@@
 \end{example}
-
-\TODO{Fin -- Exemple 2}
 
@@
 
-\TODO{Debut -- Example 3}
 \begin{example} 
@@
 \ref{Fig:SpecOA}.
-\begin{figure}[h]
+\begin{figure}[!t]
  \centering
@@
 \end{figure}
-We can easily check that the automata on Fig.\ref{Fig:RefineOA} is a refinement of this automaton. $R=\{(r_0,s_0) \mapsto True, (r_0,s_1) \mapsto True \}$ is a simulation.
+We can easily check that this automaton simulates the one on Fig.\ref{Fig:RefineOA}.
+The simulation relation is $R=\{(r_0,s_0) \mapsto l=f, (r_0,s_1) \mapsto f=l+1\% N \}$ is a simulation. \qed
 \end{example}
-\TODO{Fin}
 
@@
 \begin{example}
+
+\texttt{prod-cons[P/producer] < simple-prod-cons[P/producer]}
 

### 2023-04-13 2021-Refinement/paper/refinementarticleV2.tex
les modifs figures + uniform. police

@@
 The example uses several kinds of data.
-Variable $m$ holds a message, message types do not need a concrete definition here.
-We additionally use arrays of messages with a syntax of the form $M[l]$ for array accesses; $M$ is an array of $N$ elements, from $0$ to $N-1$.
+Variable $\texttt{m}$ holds a message, message types do not need a concrete definition here.
+We additionally use arrays of messages with a syntax of the form $\texttt{M[l]}$ for array accesses; $\texttt{M}$ is an array of $\texttt{N}$ elements, from $0$ to $\texttt{N}-1$.
 Finally we use addition and modulo operation ($\%$) on integers.
@@
 The buffer reacts to a push from $\texttt{P}$ and enqueues it.
-Similarly, whenever it  $\texttt{Q}$ pops an element, it dequeues it.
+Similarly, whenever   $\texttt{Q}$ pops an element, it dequeues it.
 Additionally, whenever $\texttt{Q}$ produces an item, it is exposed as an external observable  $\texttt{print}$ action.
@@
 \begin{example} 
- Fig. \ref{Fig:procandcons} shows a producer automaton  and a consumer  automaton that can be used  to fill the holes $P$ and $Q$ of \texttt{prod-cons} defined in Example~\ref{ex:fifo-system}.
+ Fig.
+\ref{Fig:procandcons} shows a producer automaton  and a consumer  automaton that can be used  to fill the holes $\texttt{P}$ and $\texttt{Q}$ of \texttt{prod-cons} defined in Example~\ref{ex:fifo-system}.
  \begin{figure}[!ht]
@@
 The composition consists of two states (the product of the states of both automata).
-The transitions from one state to another come from  the synchronisation  of the transitions of the encompassing automaton with those of the producer filling the hole $P$.
+The transitions from one state to another come from  the synchronisation  of the transitions of the encompassing automaton with those of the producer filling the hole $\texttt{P}$.
 Transitions involving \texttt{Q} remain unchanged.
@@
 
-  \draw (1) edge[align=center] node[below]{\OT{}{}{\alpha(x)}{h\mapsto\beta(x)}{x<0}{y\leftarrow -x}}  (2);
-  \draw (1) edge[align=center] node[above]{\OT{}{}{\alpha(x)}{h\mapsto\beta(x)}{x\geq 0}{y\leftarrow x}} (3);
+  \draw (1) edge[align=center] node[below]{\OT{}{}{\alpha(x)}{\{h\mapsto\beta(x)\}}{[x<0]}{(y\leftarrow -x)}}  (2);
+  \draw (1) edge[align=center] node[above]{\OT{}{}{\alpha(x)}{\{h\mapsto\beta(x)\}}{[x\geq 0]}{(y\leftarrow x)}} (3);
 \end{tikzpicture}
@@
   \node[state,inner sep=5pt,minimum size=10pt,  right of=1,right=90pt] (2) {$t_2$};
-
-  \draw (1) edge[align=center] node[below]{\OT{}{}{\alpha(x)}{h\mapsto\beta(x)}{tt}{z\leftarrow x}}  (2);
+\draw (1) edge[align=center] node[below]{\OT{}{}{\alpha(x)}{\{h\mapsto\beta(x)\}}{True}{(z\leftarrow x)}}  (2);
 %  \draw (1) edge[align=center] node[above]{\OT{}{}{\alpha(x)}{h\mapsto\beta(x)}{x\geq 0}{y\leftarrow x}} (3);
@@
 Indeed, we need two transitions on the left OA to simulate a single transition on the right one.
-We should check that these two transitions cover all the cases accepted by te right hand side OA, and of course that destination states are in relation.
-Formally, fh-bisimulation is defined \cite{fhbisim} as follows:
+We should check that these two transitions cover all the cases accepted by the right hand side OA, and of course that destination states are in relation.
+Formally, FH-bisimulation is defined \cite{fhbisim} as follows:
 
@@
 \begin{example} 
-To illustrate the refinement simulation of open automata, consider a variation on the \texttt{prod-cons}.
+To illustrate the refinement simulation of open automata, consider a variation on the \texttt{prod-cons}, referred to as \texttt{Simpleprod-cons}.
 We suppose that  the two processes  \texttt{P} and  \texttt{Q} communicate through a one-place  buffer.
@@
 \end{figure}
-We can easily check that this automaton simulates the one on Fig.\ref{Fig:RefineOA}.
-The simulation relation is $R=\{(r_0,s_0) \mapsto l=f, (r_0,s_1) \mapsto f=l+1\% N \}$ is a simulation. \qed
+We can easily check that this automaton simulates the one on Fig.~\ref{Fig:RefineOA}.
+The simulation relation is $R=\{(r_0,s_0) \mapsto \texttt{l}=\texttt{f}, (r_0,s_1) \mapsto \texttt{f}=\texttt{l}+1\% \texttt{N} \}$ is a simulation. \qed
 \end{example}

### 2023-04-24 2021-Refinement/paper/refinementarticleV2.tex
examples

@@
 
-\begin{example}[\texttt{prod-cons}]\label{ex:fifo-system} As a running example, we consider a classical producer-consumer pair  interacting through FIFO buffer,  referred to as \texttt{prod-cons}.
+\begin{example}[\texttt{prod-cons}]\label{Example:fifo-system} As a running example, we consider a classical producer-consumer pair  interacting through FIFO buffer,  referred to as \texttt{prod-cons}.
 Fig.
@@
 
-\begin{example} 
- Fig.
+\begin{example} \label{Example:prodandcons} Fig.
 \ref{Fig:procandcons} shows a producer automaton  and a consumer  automaton that can be used  to fill the holes $\texttt{P}$ and $\texttt{Q}$ of \texttt{prod-cons} defined in Example~\ref{ex:fifo-system}.
@@
    \includegraphics[width=.99\textwidth]{Figures/compos-FIFO-Pro.pdf}
-   \caption{Open Automaton of the \texttt{prod-cons}[\texttt{P}/\texttt{producer}]. 
+   \caption{Open Automaton for \texttt{prod-cons}[\texttt{P}/\texttt{producer}]. 
    \label{Fig:ComposeOA}} 
@@
 
-An composable automaton cannot transform external non-determinism of the sub-automaton into internal non-determinism.
+A composable automaton cannot transform external non-determinism of the sub-automaton into internal non-determinism.
 
@@
 
-\begin{example} 
-To illustrate the refinement simulation of open automata, consider a variation on the \texttt{prod-cons}, referred to as \texttt{Simpleprod-cons}.
-We suppose that  the two processes  \texttt{P} and  \texttt{Q} communicate through a one-place  buffer.
-The  corresponding behaviour  is given by  an open automaton  depicted in Fig.
-\ref{Fig:SpecOA}.
+\begin{example} \label{example:fifo-system-one}
+To illustrate the refinement simulation of open automata, we consider a variation on the \texttt{prod-cons} example.
+Namely,  we suppose that  the two processes  \texttt{P} and  \texttt{Q} communicate through a one-place  buffer.
+The  corresponding behaviour of this simpler version of the system is specified by the    open automaton  depicted in Fig.
+\ref{Fig:SpecOA}, referred to as \texttt{Simprod-cons}.
 \begin{figure}[!t]
@@
    \includegraphics[width=.90\textwidth]{Figures/FIFOpen2.pdf}
-   \caption{Open Automation of the \texttt{prod-cons} system using one-place  buffer.  \label{Fig:SpecOA}}
+   \caption{  The \texttt{Simprod-cons} Open Automaton: \texttt{prod-cons} system using one-place  buffer.  \label{Fig:SpecOA}}
 \end{figure}
@@
 
-\begin{theorem}[Congruence]
+\begin{example}  Consider again the \texttt{prod-cons}  \texttt{Simprod-cons}  automata given in examples above.
+Since we have \texttt{prod-cons} $\leq_{\{\texttt{P,Q}\}}$ \texttt{simprod-cons},  hence according to Theorem \ref{thm:ContextRefinement}, we get
+\texttt{prod-cons[P/producer]} $\leq_{\{\texttt{Q}\}}$  \texttt{Simprod-cons[P/producer]}.
+This can be verified by comparing the behaviour of the automaton of the figure Fig.~\ref{Fig:ComposeOA} and the automaton resulting  from the composition of the \texttt{Simprod} and  \texttt{producer} automata.\qed
+\end{example}
+
+\begin{theorem}[Congruence]\label{thm:CongurenceRefinement}
 Let $A_1$, $A_2$ and $A_3$ be three open automata with $\wrel{A_2}{A_3}{H}$. 
@@
 
-\begin{example}
-
-\texttt{prod-cons[P/producer] < simple-prod-cons[P/producer]}
-
-The composition of the refined \texttt{database} and the \texttt{counter} is again an open automata, depicted in Fig.~\ref{Fig:ComposeRefine}.
-As stated by the theorem,  it can easily be verified that this automaton is a refinement of the automaton of the figure Fig.~\ref{Def:CompOA}, i.e.
-the automaton resulting from the composition of the abstract \texttt{database}.
-\end{example}
+As an example of the use of this theorem, consider a refined version of the producer process of Example ~\ref{Example:prodandcons} that we  refer to as $\texttt{producer}^{*}$.
+According to  Theorem \ref{thm:CongurenceRefinement}, we have
+\texttt{prod-cons[P/producer]} $\leq_{\{\texttt{Q}\}}$  \texttt{prod-cons[P/$\texttt{producer}^{*}$]}; as well as \texttt{Simprod-cons[P/producer]} $\leq_{\{\texttt{Q}\}}$  \texttt{Simprod-cons[P/$\texttt{producer}^{*}$]}.
 

### 2023-04-25 2021-Refinement/paper/refinementarticleV2.tex
refinements

@@
 In the following definition we add a parameter $H$ which is the set of holes tracked by the refinement relation and adapt the definition by ignoring actions of the holes that are not in $H$.
-\begin{definition}[Open automata refinement]\label{Def:OA-Refinement}
+\begin{definition}[Hole-tracking simulation]\label{Def:OA-Refinement}
 For two open automata\\ \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a refinement of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a relation on configurations $R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that:
@@
 
-\begin{example} It is easy to see the  open automaton of Fig.~\ref{Fig:RefineOA} is a refinement the open automaton of Fig.~\ref{Fig:SpecOA} according to this definition.
-\end{example}
+%\begin{example} It is easy to see the  open automaton of Fig.~\ref{Fig:RefineOA} is a refinement the open automaton of Fig.~\ref{Fig:SpecOA} according to this definition.
+%\end{example}
+
+\begin{property}[Relating simulations]\label{lem-sim-sim}
+Hole-equal simulation is a particular case of hole-tracking refinement when  $J_1=J_2=H$.
+\end{property}
+\TODO{potential ex 4: check if the example with a hole filled is a simulation of the example with holes? at least state \texttt{prod-cons} $\leq_{\{\texttt{P,Q}\}}$ \texttt{simprod-cons}}
 
@@
 
-\begin{lemma}[Tracked holes] By construction, if an automaton is the refinement of another one, it is also a refinement by tracking less holes.
+\begin{property}[Tracked holes] By construction, if an automaton is the refinement of another one, it is also a refinement by tracking less holes.
 \[\wrel{A_1}{A_2}{H} \land H'\subseteq H \implies \wrel{A_1}{A_2}{H'}\]
-\end{lemma}
+\end{property}
 
@@
 We now  state the properties of our refinement relations, proofs of the properties can be found in the appendices.
-We express these properties in terms of open automata refinement because hole-equal simulation is a particular case of Definition~\ref{Def:OA-Refinement} when  $J_1=J_2=H$, and thus all the properties shown here are trivially true for hole-equal simulation.
+We express these properties in terms of hole-tracking simulation because, thanks to Property~\ref{lem-sim-sim}   all the properties  of hole-tracking simulation are also valid  for hole-equal simulation
 The first crucial property of  refinement  is that it is  a  preorder on the set of open automata. This property enables stepwise refinement.
@@
 
-\begin{example}  Consider again the \texttt{prod-cons}  \texttt{Simprod-cons}  automata given in examples above.
+\begin{example}  Consider again the \texttt{prod-cons} and \texttt{Simprod-cons}  automata given in the examples above.
 Since we have \texttt{prod-cons} $\leq_{\{\texttt{P,Q}\}}$ \texttt{simprod-cons},  hence according to Theorem \ref{thm:ContextRefinement}, we get

### 2023-04-25 2021-Refinement/paper/refinementarticleV2.tex
simulation

@@
 
-\begin{theorem}[Refinement is a preorder]
-Refinement   is reflexive  and  transitive:  it  is  a  preorder on the set of open automata.
+\begin{theorem}[Simulation is a preorder]
+Hole-tracking simulation
+   is reflexive  and  transitive:  it  is  a  preorder on the set of open automata.
 \end{theorem}
@@
 \texttt{prod-cons[P/producer]} $\leq_{\{\texttt{Q}\}}$  \texttt{Simprod-cons[P/producer]}. 
-This can be verified by comparing the behaviour of the automaton of the figure Fig.~\ref{Fig:ComposeOA} and the automaton resulting  from the composition of the \texttt{Simprod} and  \texttt{producer} automata.\qed
+The behaviour of \texttt{prod-cons[P/producer]} is shown Fig.~\ref{Fig:ComposeOA}.
+The automaton resulting  from the composition of  \texttt{Simprod} and \texttt{producer} is bigger and not shown here. \qed
 \end{example}
@@
 
-As an example of the use of this theorem, consider a refined version of the producer process of Example ~\ref{Example:prodandcons} that we  refer to as $\texttt{producer}^{*}$.
+Consequently, as the simulation is transitive \TODO{TODO Thm 4}
+
+\begin{example}
+As an example of the use of this theorem, if we design a refined version of the producer process of Example~\ref{Example:prodandcons} and call it $\texttt{producer}^{*}$.
 According to  Theorem \ref{thm:CongurenceRefinement}, we have
-\texttt{prod-cons[P/producer]} $\leq_{\{\texttt{Q}\}}$  \texttt{prod-cons[P/$\texttt{producer}^{*}$]}; as well as \texttt{Simprod-cons[P/producer]} $\leq_{\{\texttt{Q}\}}$  \texttt{Simprod-cons[P/$\texttt{producer}^{*}$]}.
+\texttt{prod-cons[P/producer]} $\leq_{\{\texttt{Q}\}}$  \texttt{prod-cons[P/$\texttt{producer}^{*}$]}; as well as \texttt{prod-cons[P/producer]} $\leq_{\{\texttt{Q}\}}$  \texttt{Simprod-cons[P/$\texttt{producer}^{*}$]}.
+
+\end{example}
 

### 2023-04-25 2021-Refinement/paper/refinementarticleV2.tex
OA

@@
 
+* choisir terminologie: refinement or simulation
+
+* open automata  / Open Automata -> only use open automata or OA.
+
 * positioning
 
+* format according to conf
+
 * global rewriting (partly done)
 
-* choisir terminologie: refinement or simulation
-
-Automata are convenient for specifying and verifying systems, but most automata definitions allow only the specifications of finite closed systems.
+Automata are convenient for specifying` and verifying systems, but most automata definitions allow only the specifications of finite closed systems.
 Indeed those systems are the ones we can verify efficiently, but programming often consists in writing open systems that should be interfaced with others, and with potentially unbound behaviours (at least statically).
@@
 
-Open automata were defined as a way to provide a semantics for open parameterized hierarchical LTSs used in verification tools and called \emph{pNets}.
-An open automaton \cite{henrio:01299562} is a classical automaton with variables and holes.
+Open automata (that we abbreviate OA) were defined as a way to provide a semantics for open parameterized hierarchical LTSs used in verification tools and called \emph{pNets}.
+An OA \cite{henrio:01299562} is a classical automaton with variables and holes.
 Variables make automata symbolic and allow them to encode infinite state systems.
@@
 
-In previous works \cite{fhbisim,wang:03126313} a bisimulation relation was defined for open automata and open parameterized hierarchical LTSs.
+In previous works \cite{fhbisim,wang:03126313} a bisimulation relation was defined for OA and open parameterized hierarchical LTSs.
 It has already good properties relatively to bisimulation, but refinement relations were not studied.
 
-This article first introduces open automata that were defined in  \cite{henrio:01299562}. %,  but compared to previous works, we 
-and additionaly defines the composition of open automata.
-Then we define  a refinement relation for open automata that has the following characteristics:
+This article first introduces OA that were defined in  \cite{henrio:01299562}. %,  but compared to previous works, we 
+and additionaly defines the composition of OA.
+Then we define  a refinement relation for OA that has the following characteristics:
 \begin{itemize}
@@
 \item Good properties relatively to composition: we prove here that filling the same hole  with the same automaton preserves the refinement relation.
-\item Ability to take into account both composition and transitivity: this is a challenge because composition changes the set of holes of the open automaton and refinement takes into account the actions of the holes.
+\item Ability to take into account both composition and transitivity: this is a challenge because composition changes the set of holes of the OA and refinement takes into account the actions of the holes.
 \end{itemize}
@@
 First we define a refinement that relates two automata with the same holes, which allows us to focus on the automaton aspect.
-Second we introduce a relation that relates two automata with different sets of holes, which allows us to take into account the open nature of open automata, and to deal with composition.
+Second we introduce a relation that relates two automata with different sets of holes, which allows us to take into account the open nature of OA, and to deal with composition.
 Properties of the refinement are stated and proven on the second, more general version of the relation, they are thus also valid for the first simpler refinement relation.
@@
 Section~\ref{sec:background} recalls the definition of open automata and defines their composition. 
-We  then  define a refinement relation for open automata, first only considering two automata with the same set of holes in Section~\ref{sec:refinement} and generalize it to automata with a different set of holes in Section~\ref{sec:holes}.
+We  then  define a refinement relation for OA, first only considering two automata with the same set of holes in Section~\ref{sec:refinement} and generalize it to automata with a different set of holes in Section~\ref{sec:holes}.
 Section~\ref{sec:prop} is dedicated to formalize and prove basic properties of refinement in ; here we prove that refinement is a preorder and has good composition property.
@@
 This section presents our notations and the principles of automata.
-Except for minor changes in the notations, compared to previous works~\cite{fhbisim} the only new contribution is the definition of a composition operator for open automata.
+Except for minor changes in the notations, compared to previous works~\cite{fhbisim} the only new contribution is the definition of a composition operator for OA.
 %
@@
 
-\subsection{Open Automata}\label{sec:def}
- Open automata (abbreviated OA) are labelled transition systems with variables  that can be used to compose other automata: they are made of transitions that are dependent on the actions of ``holes'', a composition operation consists in filling a hole with another automaton to obtain a more complex automaton.
+\subsection{Open Automata (OA)}\label{sec:def}
+ OA  are labelled transition systems with variables  that can be used to compose other automata: they are made of transitions that are dependent on the actions of ``holes'', a composition operation consists in filling a hole with another automaton to obtain a more complex automaton.
 The variables makes the OA symbolic, and the holes allow for a partial definition of the behaviour.
 
-\begin{definition}[Open transition, Open automaton (OA)]
+\begin{definition}[Open transition, Open automaton]
 An \emph{open automaton} is a tuple \(\OAg\) with \(S\) a set of states, \(s_0 \in S\) the initial state, \(V\) the finite set of variable names, \(\sigma_0: V \to \values\) the initial valuation of variables, \(J\) the set of hole names and \(T\) the set of open transitions.
@@
 
-\begin{example}[\texttt{prod-cons}]\label{Example:fifo-system} As a running example, we consider a classical producer-consumer pair  interacting through FIFO buffer,  referred to as \texttt{prod-cons}.
+\begin{example}[\texttt{prod-cons}]\label{Example:fifo-system} As a running example, we consider a classical producer-consumer pair  interacting through FIFO buffer, named \texttt{prod-cons}.
 Fig.
@@
 
-The open automaton  modelling the behaviour of such a system  using an  unbounded circular/ring buffer is depicted in Fig.
+The OA  modelling the behaviour of such a system  using an  unbounded circular/ring buffer is depicted in Fig.
 \ref{Fig:RefineOA}.
@@
 
-The open automaton on Fig.
+The OA on Fig.
 \ref{Fig:ComposeOA} is the composition of the system in Fig.~\ref{Fig:RefineOA} and the producer in Fig.
@@
 To do so we will suppose that the variables of the two OA are disjoint (a renaming of variables may have to be applied before comparing OA states).
-\begin{definition}[Relation on OA configurations] Suppose $V_1$ and $V_2$ are disjoint.
+\begin{definition}[Relation on open automata configurations] Suppose $V_1$ and $V_2$ are disjoint.
 A relation on configurations of two OA \(\OAg[1]\) and \(\OAg[2]\) is a function \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
@@
 %   \mathcal{T}_1 \myrangle$ and $A_2 = \mylangle J,\mathcal{S}_2,t_0,V_2, \mathcal{T}_2 \myrangle$
-   are open automata with identical holes of the same sort, with disjoint sets of variables ($V_1\cap V_2=\emptyset$).
+   are OA with identical holes of the same sort, with disjoint sets of variables ($V_1\cap V_2=\emptyset$).
 
@@
 \subsection{Reachability}
-We finally define a predicate abstracting state reachability for open automata, it  allows us to reason on reachable states in an automaton.
-It can alternatively be seen as an abstraction of the reachable states under the form of a predicate that must stay verified along the execution of the open automaton.
+We finally define a predicate abstracting state reachability for OA, it  allows us to reason on reachable states in an automaton.
+It can alternatively be seen as an abstraction of the reachable states under the form of a predicate that must stay verified along the execution of the OA.
 \begin{definition}[Reachability] \label{Def:Reach}
-For any open automata \(A = \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is any predicate on states that is valid on initial state, and preserved across transitions:
+For any OA \(A = \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is any predicate on states that is valid on initial state, and preserved across transitions:
 \[\sigma_0 \vdash \reach{A}\mpar{s_0}\quad\land\quad\forall t = \OTg \in T, \fvars{t} \vdash \left(\reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}\right)\]
@@
 Reachability takes into account all paths, and can over-approximate the reachable configurations. 
-From an automation point of view, finding the most precise reachability predicate for a given automata is not decidable because of the symbolic nature of open automata, but only an over-approximation is necessary.
+From an automation point of view, finding the most precise reachability predicate for a given automata is not decidable because of the symbolic nature of OA, but only an over-approximation is necessary.
 
@@
 
-Similarly to FH-bisimulation~\cite{fhbisim} we are interested  in finding relations between configurations of two open automata that contain variables and holes. 
+Similarly to FH-bisimulation~\cite{fhbisim} we are interested  in finding relations between configurations of two OA that contain variables and holes. 
 We rely on a classical notion of simulation inspired from~\cite{fhbisim}.
@@
 However here we want to build a refinement relation that  also guarantees that no deadlock is introduced when refining the automaton, this property is quite frequent in refinement relation, and referred to as \emph{lack of new deadlocks}~\cite{Kouchnarenko:2007} or \emph{complete simulation}~\cite{sangiorgi:bisim-coind12}.
-The notion of deadlock should however be specialized to our open automata.
+The notion of deadlock should however be specialized to our OA.
 Indeed, the possible transitions are better characterized by the guards of the outgoing transitions from a given state, rather than the simple existence of a transition.
@@
 The third condition ensures that the refinement relation prevents the introduction of deadlocks.
-Our definition captures a simple kind of sub-classing of open automata with the same holes. It is more expressive than a strict simulation since it matches a transition with a family of transitions. 
-With such a relation we are able to check the refinement between two open automata with the same level of abstraction but specified differently, for example, by duplicating states, removing transitions,  reinforcing  guards, modifying variables, etc.
+Our definition captures a simple kind of sub-classing of OA with the same holes. It is more expressive than a strict simulation since it matches a transition with a family of transitions. 
+With such a relation we are able to check the refinement between two OA with the same level of abstraction but specified differently, for example, by duplicating states, removing transitions,  reinforcing  guards, modifying variables, etc.
 We will show in Section~\ref{sec:prop} that this refinement relation has good properties in terms of transitivity, compositionality, and reflexivity.
@@
 \begin{example} \label{example:fifo-system-one}
-To illustrate the refinement simulation of open automata, we consider a variation on the \texttt{prod-cons} example.
+To illustrate the refinement simulation of OA, we consider a variation on the \texttt{prod-cons} example.
 Namely,  we suppose that  the two processes  \texttt{P} and  \texttt{Q} communicate through a one-place  buffer.
-The  corresponding behaviour of this simpler version of the system is specified by the    open automaton  depicted in Fig.
+The  corresponding behaviour of this simpler version of the system is specified by the    OA  depicted in Fig.
 \ref{Fig:SpecOA}, referred to as \texttt{Simprod-cons}.
@@
 
-The refinement relation defined above is insufficient in the setting of composition which is the main advantage of the open automaton-based approach.
+The refinement relation defined above is insufficient in the setting of composition which is the main advantage of the OA-based approach.
 Indeed, it should be possible to refine an automaton by filling its hole, providing a concrete view of a part of the application that was not specified originally.
@@
 An automatic tool would only need to find an over approximation of reachability to reason on composition that is compatible with deadlock reduction.
-We call \emph{non-blocking composition} a composition that can be safely be used to compose open automata that are involved in a deadlock reducing relation.
+We call \emph{non-blocking composition} a composition that can be safely be used to compose OA that are involved in a deadlock reducing relation.
 
@@
 \begin{definition}[Non-blocking composition] \label{Def:Non-block}
-Let \(A_1 \defobject \OAg[1]\), \( A_2 \defobject \OAg[1]\) be two open automata.
+Let \(A_1 \defobject \OAg[1]\), \( A_2 \defobject \OAg[1]\) be two OA.
 Let \(A = A_1\subst{A_2}{k}\) and $A= \OAg$.
@@
 One major challenge in the extension of refinement to different sets of holes is to maintain a form of transitivity while being able to take into account the actions of some of the holes.
-A naive definition of refinement would ensure that only the holes that are identical in the two open automata are taken into account in the simulation.
+A naive definition of refinement would ensure that only the holes that are identical in the two OA are taken into account in the simulation.
 Unfortunately considering all the common holes does not ensure transitivity of the simulation for the following reason.
@@
 \begin{definition}[Hole-tracking simulation]\label{Def:OA-Refinement}
-For two open automata\\ \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a refinement of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a relation on configurations $R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that:
+For two OA\\ \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a refinement of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a relation on configurations $R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that:
 \item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
@@
 We express these properties in terms of hole-tracking simulation because, thanks to Property~\ref{lem-sim-sim}   all the properties  of hole-tracking simulation are also valid  for hole-equal simulation
-The first crucial property of  refinement  is that it is  a  preorder on the set of open automata. This property enables stepwise refinement.
+The first crucial property of  refinement  is that it is  a  preorder on the set of OA. This property enables stepwise refinement.
 
@@
 Hole-tracking simulation
-   is reflexive  and  transitive:  it  is  a  preorder on the set of open automata.
+   is reflexive  and  transitive:  it  is  a  preorder on the set of OA.
 \end{theorem}
@@
  refinement is compositional in the sense that it is sufficient to prove refinement for the composed automata separately to obtain a refinement relation.
-The second part,  proving that placing in the same context two open automata in refinement, we obtain two open automata in refinement is left for future works.
+The second part,  proving that placing in the same context two OA in refinement, we obtain two OA in refinement is left for future works.
 %
@@
 \begin{theorem}[Context refinement]\label{thm:ContextRefinement}
-Let $A_1$, $A_2$ and $A_3$ be three open automata with $\wrel{A_1}{A_2}{H}$. 
+Let $A_1$, $A_2$ and $A_3$ be three OA with $\wrel{A_1}{A_2}{H}$. 
 Let $J_3$ be the set of holes of $A_3$ and suppose that $k \in H$.
@@
 \begin{theorem}[Congruence]\label{thm:CongurenceRefinement}
-Let $A_1$, $A_2$ and $A_3$ be three open automata with $\wrel{A_2}{A_3}{H}$. 
+Let $A_1$, $A_2$ and $A_3$ be three OA with $\wrel{A_2}{A_3}{H}$. 
   Let $J_3$ be the set of holes of $A_3$ and suppose that \(k \in H\). Suppose additionally that the composition $A_1\subst{A_2}{k}$ is non-blocking.
@@
 
-Previous works on open automata focused on equivalence relations compatible with composition.
-In  \cite{10.1145/3372884.3373161}, a computable bisimulation is introduced, while in \cite{fhbisim} is introduced a weak version of the bisimulation on open automata. 
+Previous works on OA focused on equivalence relations compatible with composition.
+In  \cite{10.1145/3372884.3373161}, a computable bisimulation is introduced, while in \cite{fhbisim} is introduced a weak version of the bisimulation on OA. 
 In this paper we tackle the refinement relation in the form of simulation, as is the case for the corresponding relations on labelled transition systems \cite{10.1007/3-540-46428-X_19}.
@@
 In this article we investigated the notion of refinement for a symbolic and open model: open automata. 
-Open automata are convenient to model parallel systems that are parameterised both by the use of variables and by the possibility to compose automata.
+OA are convenient to model parallel systems that are parameterised both by the use of variables and by the possibility to compose automata.
 The refinement relation first relies on a simulation relation between the specification and its refinement, but it also specifies that the refined process must follow the behaviour of the specification, not only at every compatible state but also along any trace.
@@
 
-We have to prove that the relation $R_{13}$ satisfies the three conditions of the definition of a refinement of open automata.
+We have to prove that the relation $R_{13}$ satisfies the three conditions of the definition of a refinement of OA.
 \begin{enumerate}
@@
 \[\sigma_{01} \uplus \sigma_{03} \vdash R_{13} \mpar{s_{01}, s_{03}}\]
-By knowing that substitutions only have an effect on the variables of the open automaton they belong to, they also produce terms containing only variables of the open automaton they belong to.
-We have:
+By knowing that substitutions only have an effect on the variables of the OA they belong to, they also produce terms containing only variables of the OA they belong to. We have:
 \begin{align*}
@@
 
-First, according to the relation between $A_1$ and $A_2$ open automata,  for all $\mpar{s_1, s_{2p}} \in S_1\times S_2$  we have:
+First, according to the relation between $A_1$ and $A_2$ OA,  for all $\mpar{s_1, s_{2p}} \in S_1\times S_2$  we have:
 \begin{multline*}
@@
 \end{multline*}
-Second, according to the relation between $A_2$ and $A_3$ open automata, for all $\mpar{s_{2p},s_3} \in S_2\times S_3$  we have:
+Second, according to the relation between $A_2$ and $A_3$ OA, for all $\mpar{s_{2p},s_3} \in S_2\times S_3$  we have:
 \begin{multline*}
@@
 Let us denote by $A_{13}$ (resp.
-$A_{23}$) the open automaton resulting from $A_1\subst{A_3}{k}$ (resp.
-$A_2\subst{A_3}{k}$),  to prove the theorem it is sufficient to prove that there exists a relation between states of the two open automata that satisfies the conditions of the Definition \ref{Def:OA-Refinement}.
+$A_{23}$) the OA resulting from $A_1\subst{A_3}{k}$ (resp.
+$A_2\subst{A_3}{k}$),  to prove the theorem it is sufficient to prove that there exists a relation between states of the two OA that satisfies the conditions of the Definition \ref{Def:OA-Refinement}.
 
@@
 
-Recall that by definition of composition and open automata refinement we have: 
+Recall that by definition of composition and OA refinement we have: 
 \begin{align*}
@@
 Let us denote by $A_{12}$ (resp.
-$A_{13}$) the open automaton resulting from $A_1\subst{A_2}{k}$ (resp.
-$A_1\subst{A_3}{k}$),  to prove the theorem it is sufficient to prove that there exists a relation between states of the two open automata that satisfies the conditions of the Definition \ref{Def:OA-Refinement}.
+$A_{13}$) the OA resulting from $A_1\subst{A_2}{k}$ (resp.
+$A_1\subst{A_3}{k}$),  to prove the theorem it is sufficient to prove that there exists a relation between states of the two OA that satisfies the conditions of the Definition \ref{Def:OA-Refinement}.
 
@@
 	\end{multline*}
-By definition of composition and open automata refinement we have: 
+By definition of composition and OA refinement we have: 
 \begin{align*}

### 2023-04-28 2021-Refinement/paper/refinementarticleV2.tex
qques corrections

@@
    \includegraphics[width=.99\textwidth]{Figures/FIFORing.pdf}
-   \caption{Open Automaton for the \texttt{prod-cons} system using FIFO circular buffer.
+   \caption{Open automaton for the \texttt{prod-cons} system using FIFO circular buffer.
     \label{Fig:RefineOA}} 
@@
 
-OA are partially specified automata, that partiality comes  from the holes.
+OA are partially specified automata, the partiality arises  from the holes.
 A hole can be seen as a port in which we can plug an OA.
@@
 \begin{example} \label{Example:prodandcons} Fig.
-\ref{Fig:procandcons} shows a producer automaton  and a consumer  automaton that can be used  to fill the holes $\texttt{P}$ and $\texttt{Q}$ of \texttt{prod-cons} defined in Example~\ref{ex:fifo-system}.
+\ref{Fig:procandcons} shows a producer automaton  and a consumer  automaton that can be used  to fill the holes $\texttt{P}$ and $\texttt{Q}$ of \texttt{prod-cons} defined in Example~\ref{Example:fifo-system}.
  \begin{figure}[!ht]
@@
 \ref{Fig:ComposeOA} is the composition of the system in Fig.~\ref{Fig:RefineOA} and the producer in Fig.
-\ref{Fig:procandcons}.
+\ref{Fig:procandcons} (left).
 The composition consists of two states (the product of the states of both automata).
@@
    \includegraphics[width=.99\textwidth]{Figures/compos-FIFO-Pro.pdf}
-   \caption{Open Automaton for \texttt{prod-cons}[\texttt{P}/\texttt{producer}]. 
+   \caption{Open automaton for \texttt{prod-cons}[\texttt{P}/\texttt{producer}]. 
    \label{Fig:ComposeOA}} 
@@
 \subsection{Relations between open automata}
-A relation (bisimulation, refinement, etc.) between OA requires to compare their states.
-To do so we will suppose that the variables of the two OA are disjoint (a renaming of variables may have to be applied before comparing OA states).
+Establishing semantic equivalences and refinement relations between different OA requires  to compare their states.
+For this purpose, we suppose that the variables of the two OA are disjoint (a renaming of variables may have to be applied before comparing OA states).
 \begin{definition}[Relation on open automata configurations] Suppose $V_1$ and $V_2$ are disjoint.
@@
 %\TODO{C'est etrange, la formulation "the variables they refer to", comme il n'y a plus de variables d'etat... +1}
-The idea is that two states are related depending on the state of the automaton, i.e. if the variables of the OA verify a certain formula. 
-In other words, for each pair of states, a boolean formula that may refer to the  variables of each of the two OA states whether the two states are related or not.
+The idea is that two states are related depending on the satisfiability of the expression relying their variables i.e., if the variables of the OA verify a certain formula. 
+In other words, for each pair of states is attached a boolean formula that may refer to the  variables of each of the two OA states, stating whether the two states are related or not.
 Additionally, we may check that initial states of the automata are related by checking that: \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\).
@@
 
-  \draw (1) edge[align=center] node[below]{\OT{}{}{\alpha(x)}{\{h\mapsto\beta(x)\}}{[x<0]}{(y\leftarrow -x)}}  (2);
-  \draw (1) edge[align=center] node[above]{\OT{}{}{\alpha(x)}{\{h\mapsto\beta(x)\}}{[x\geq 0]}{(y\leftarrow x)}} (3);
+  \draw (1) edge[align=center] node[below]{\OT{}{}{\alpha(x)}{\{h\mapsto\beta(x)\}}{x<0}{(y\leftarrow -x)}}  (2);
+  \draw (1) edge[align=center] node[above]{\OT{}{}{\alpha(x)}{\{h\mapsto\beta(x)\}}{x\geq 0}{(y\leftarrow x)}} (3);
 \end{tikzpicture}
@@
 
-Similarly to FH-bisimulation~\cite{fhbisim} we are interested  in finding relations between configurations of two OA that contain variables and holes. 
+Similarly to FH-bisimulation~\cite{fhbisim} we are interested  in finding refinement relations between configurations of two OA that contain variables and holes.
+When dealing with open systems it is common to define refinement in terms of a simulation relation.
 We rely on a classical notion of simulation inspired from~\cite{fhbisim}.
@@
 Namely,  we suppose that  the two processes  \texttt{P} and  \texttt{Q} communicate through a one-place  buffer.
-The  corresponding behaviour of this simpler version of the system is specified by the    OA  depicted in Fig.
-\ref{Fig:SpecOA}, referred to as \texttt{Simprod-cons}.
+Fig.
+\ref{Fig:SpecOA} shows the OA modelling this simpler version of the system, that we refer to as \texttt{Simprod-cons}.
 \begin{figure}[!t]
@@
    \includegraphics[width=.90\textwidth]{Figures/FIFOpen2.pdf}
-   \caption{  The \texttt{Simprod-cons} Open Automaton: \texttt{prod-cons} system using one-place  buffer.  \label{Fig:SpecOA}}
+   \caption{  The \texttt{Simprod-cons} Open automaton: the system using one-place  buffer.  \label{Fig:SpecOA}}
 \end{figure}
-We can easily check that this automaton simulates the one on Fig.~\ref{Fig:RefineOA}.
-The simulation relation is $R=\{(r_0,s_0) \mapsto \texttt{l}=\texttt{f}, (r_0,s_1) \mapsto \texttt{f}=\texttt{l}+1\% \texttt{N} \}$ is a simulation. \qed
+We can easily check that this automaton simulates the one of Fig.~\ref{Fig:RefineOA}.
+Indeed, one can see that  $R=\{(r_0,s_0) \mapsto \texttt{l}=\texttt{f}, (r_0,s_1) \mapsto \texttt{f}=\texttt{l}+1\% \texttt{N} \}$ is  a candidate simulation 
+relation. It follows that  \texttt{prod-cons} $\leq$ \texttt{simprod-cons}. \qed
 \end{example}
@@
 \begin{definition}[Non-blocking composition] \label{Def:Non-block}
-Let \(A_1 \defobject \OAg[1]\), \( A_2 \defobject \OAg[1]\) be two OA.
-Let \(A = A_1\subst{A_2}{k}\) and $A= \OAg$.
-
+Let \(A_1 \defobject \OAg[1]\) and \( A_2 \defobject \OAg[2]\) be two OA.
+Let $A= \OAg$ be the OA resulting from the composition \(A = A_1\subst{A_2}{k}\). 
 The composition \(A_1\subst{A_2}{k}\) is non-blocking if   \(A \) has a reachability predicate such that, for each reachable configuration, if there is a possible transition in \(A_1\) then there is a possible transition in \(A\):
 \begin{multline*}
- \forall s = \mpar{s_1, s_2} \in S, V \uplus \biguplus_\subbox{t \in \fOT{s_1}} \fvars{t} \vdash \\ \left(\reach{A}\mpar{s} \wedge \bigvee_\subbox{t \in \fOT{s_1}} \fguard{t} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \right)
+ \forall s = \mpar{s_1, s_2} \in S, V \uplus \biguplus_\subbox{t \in \fOT{s_1}} \fvars{t} \vdash  \left(\reach{A}\mpar{s} \wedge \bigvee_\subbox{t \in \fOT{s_1}} \fguard{t} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \right)
 \end{multline*}
@@
 \end{property}
+\begin{example} Consider the automata of examples \ref{Example:fifo-system} and \ref{example:fifo-system-one}.
+As we saw above, \texttt{prod-cons} $\leq$ \texttt{simprod-cons}, therefore \texttt{prod-cons} $\leq_{\{\texttt{P,Q}\}}$ \texttt{simprod-cons}.
+\end{example}
 \TODO{potential ex 4: check if the example with a hole filled is a simulation of the example with holes? at least state \texttt{prod-cons} $\leq_{\{\texttt{P,Q}\}}$ \texttt{simprod-cons}}
@@
 Let $J_3$ be the set of holes of $A_3$ and suppose that $k \in H$.
-Suppose that \(k \in H\) and that \(A_1\subst{A_3}{k}\) is non-blocking.
+Suppose additionally that  \(A_1\subst{A_3}{k}\) is non-blocking.
 We have: \[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{J_3 \uplus H \setminus \mbrc{k}}\]
 \end{theorem}
-
-Pictorially, the theorem states the following result:
-
-\begin{center}
-\includegraphics[scale=0.7]{Figures/Thm2intuition}
-\end{center}
 
@@
 
+\RAB{Pourquoi on parle bisimulation??}
 The bisimulation relation that we consider is the one that makes $A_1$ and $A_2$ bisimilar, complemented with identity of configurations for $A_3$.
@@
 \begin{example}  Consider again the \texttt{prod-cons} and \texttt{Simprod-cons}  automata given in the examples above.
-Since we have \texttt{prod-cons} $\leq_{\{\texttt{P,Q}\}}$ \texttt{simprod-cons},  hence according to Theorem \ref{thm:ContextRefinement}, we get
-\texttt{prod-cons[P/producer]} $\leq_{\{\texttt{Q}\}}$  \texttt{Simprod-cons[P/producer]}. 
-The behaviour of \texttt{prod-cons[P/producer]} is shown Fig.~\ref{Fig:ComposeOA}.
+Since  \texttt{prod-cons} $\leq_{\{\texttt{P,Q}\}}$ \texttt{simprod-cons},  then according to Theorem \ref{thm:ContextRefinement},
+\texttt{prod-cons[producer/P]} $\leq_{\{\texttt{Q}\}}$  \texttt{Simprod-cons[producer/P]}. 
+The automaton of \texttt{prod-cons[producer/P]} is shown in Fig.~\ref{Fig:ComposeOA}.
 The automaton resulting  from the composition of  \texttt{Simprod} and \texttt{producer} is bigger and not shown here. \qed
@@
 Let $A_1$, $A_2$ and $A_3$ be three OA with $\wrel{A_2}{A_3}{H}$. 
-  Let $J_3$ be the set of holes of $A_3$ and suppose that \(k \in H\). Suppose additionally that the composition $A_1\subst{A_2}{k}$ is non-blocking.
+  Let $J_1$ be the set of holes of $A_1$ and suppose that \(k \in J_1\). Suppose additionally that the composition $A_1\subst{A_2}{k}$ is non-blocking.
 We have: \[\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{J_1 \uplus H \setminus \mbrc{k}}\]
@@
 Consequently, as the simulation is transitive \TODO{TODO Thm 4}
+We can state the following theorem: 
+\begin{theorem}[Composability]\label{thm:Composability}
+Let $A_1$, $A_2$, $A_3$ and $A_4$ be four OA with $\wrel{A_1}{A_2}{H}$ and $\wrel{A_3}{A_4}{H'}$.
+Let $J_1$ and $J_2$ be the set of holes of $A_1$ and $A_2$ resp.
+and suppose that \(k \in J_1 \cap J_2\).
+We have: \[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_4}{k}}{J_1 \uplus J_2 \uplus J_3 \uplus J_4 \uplus H \uplus H'\setminus \mbrc{k}}\]
+\end{theorem}
 
 \begin{example}
-As an example of the use of this theorem, if we design a refined version of the producer process of Example~\ref{Example:prodandcons} and call it $\texttt{producer}^{*}$.
-According to  Theorem \ref{thm:CongurenceRefinement}, we have
-\texttt{prod-cons[P/producer]} $\leq_{\{\texttt{Q}\}}$  \texttt{prod-cons[P/$\texttt{producer}^{*}$]}; as well as \texttt{prod-cons[P/producer]} $\leq_{\{\texttt{Q}\}}$  \texttt{Simprod-cons[P/$\texttt{producer}^{*}$]}.
-
+As an example of the use of this theorem, if we design a refined version of the producer process of Example~\ref{Example:prodandcons} called $\texttt{producer}^{\flat}$.
+According to  Theorem \ref{thm:Composability}, we have
+\texttt{prod-cons[producer/P]} $\leq_{\{\texttt{Q}\}}$  \texttt{Simprod-cons[$\texttt{producer}^{\flat}$/P]}. 
+%as well as \texttt{prod-cons[P/producer]} $\leq_{\{\texttt{Q}\}}$  \texttt{Simprod-cons[P/$\texttt{producer}^{\flat}$]}.
 \end{example}
@@
 Some works   have addressed the problem of non-introduction of blocking by composition.
-For example, in \cite{DIHEGO2020110598} it is presented a refinement relation on process algebra based on failure semantics that is basically different from the (bi)simulation\cite{10.5555/640428.640430}.
+For example, in \cite{DIHEGO2020110598} it is presented a refinement relation on process algebra based on failure semantics that is basically different from the (bi)simulation \cite{10.5555/640428.640430}.
 
@@
 \end{quote}
+
 \proof 
@@
 \section{Proof of Context Refinement (Theorem~\ref{thm:ContextRefinement})}
+
 \begin{quote}
@@
 \smallskip
+Pictorially, the theorem states the following result:
+
+\begin{center}
+\includegraphics[scale=0.7]{Figures/Thm2intuition}
+\end{center}
 
@@
 \section{Proof of Congruence}
+\begin{quote}
 Suppose $\wrel{A_2}{A_3}{H}$ and  $k \in H$.  and the composition $A_1\subst{A_2}{k}$ is non-blocking. We have: \[\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{J_1 \uplus H \setminus \mbrc{k}}\]
+\end{quote}
+\smallskip
+Pictorially, the theorem states the following result:
+
+\begin{center}
+\includegraphics[scale=0.7]{Figures/Thm2intuition}
+\end{center}
 \proof

### 2023-05-24 2021-Refinement/paper/refinementarticleV2.tex
thm 4 rephrased
coorections

@@
 
-* example a terminer
+* \st{example a terminer}
 
@@
 
-* format according to conf
+* \st{format according to conf: lncs FACS or SEFM}
 
@@
 
-In previous works \cite{fhbisim,wang:03126313} a bisimulation relation was defined for OA and open parameterized hierarchical LTSs.
+In previous works \cite{AMHEEMA:2023,wang:03126313} a bisimulation relation was defined for OA and open parameterized hierarchical LTSs.
 It has already good properties relatively to bisimulation, but refinement relations were not studied.
@@
 % TODO: this definition is a bit strange, why is Ac in the hole of Ap but the hole is in Ac and the notation is reversed?
-The composition of \(A_p = \OAg[p]\) in the hole \(k \in J_c\) of    \(A_c = \OAg[c]\) is the OA defined as follows:
+Let  \(A_c = \OAg[c]\) be a context OA and $k$ one of its holes, \(k \in J_c\). Let \(A_p = \OAg[p]\) be an OA,  the composition $A_c\subst{A_p}{k}$ is defined as follows:
 \[A_c\subst{A_p}{k} ::=  \OA{S_c \times S_p}{\mpar{s_{0c}, s_{0p}}}{V_c \uplus V_p}{\sigma_{0c} \uplus \sigma_{0p}}{J_p \uplus J_c \setminus \mbrc{k}}{T} \] \text{with }
@@
 The idea is that two states are related depending on the satisfiability of the expression relying their variables i.e., if the variables of the OA verify a certain formula. 
-In other words, for each pair of states is attached a boolean formula that may refer to the  variables of each of the two OA states, stating whether the two states are related or not.
+In other words, to each pair of states is attached a boolean formula that may refer to the  variables of each of the two OAs, stating whether the two states are related or not.
 Additionally, we may check that initial states of the automata are related by checking that: \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\).
@@
 We would like these two OA to be considered bisimilar. Both can input any $\beta(x)$ input on their hole and stores the value of $x$, emitting $\alpha(x)$ along the transition.
-The different is the way $x$ is stored.
+The difference is the way $x$ is stored.
 We can then define a configuration relation $R$ such that $R(s,s_2)$ is true and $R(t,t_2)$ holds when $z\geq 0$ and $y=z$, while $R(t',t_2)$ holds when $z< 0$ and $y=-z$.
-This illustrates relation on configuration, but also allows us to realise that bisimulation is a bit more complex than in the classical case.
+This illustrates relation on configuration, but also allows us to realise that bisimulation on OAs is a bit more complex than in the classical case.
 Indeed, we need two transitions on the left OA to simulate a single transition on the right one.
@@
 When dealing with open systems it is common to define refinement in terms of a simulation relation.
-We rely on a classical notion of simulation inspired from~\cite{fhbisim}.
+We rely on a classical notion of simulation inspired from~\cite{AMHEEMA:2023}.
 The idea is that two configurations related by a relation; if one state can do a transition, then the other can do a transition too.
-Like for bisimulation, refinement relation characterizes when two states are related, and this  characterisation is expressed as a predicate on the variables of the two automata.
+Like for bisimulation, a refinement relation characterises when two states are related, and this  characterisation is expressed as a predicate on the variables of the two automata.
 Refinement defines conditions on a predicate $R$ such that $R\mpar{s_1, s_2}$ is a predicate (possibly involving variables of the automata) that is true when the state $s_1$ of $A_1$ refines the state $s_2$ of $A_2$.
@@
 
-However here we want to build a refinement relation that  also guarantees that no deadlock is introduced when refining the automaton, this property is quite frequent in refinement relation, and referred to as \emph{lack of new deadlocks}~\cite{Kouchnarenko:2007} or \emph{complete simulation}~\cite{sangiorgi:bisim-coind12}.
-The notion of deadlock should however be specialized to our OA.
-Indeed, the possible transitions are better characterized by the guards of the outgoing transitions from a given state, rather than the simple existence of a transition.
-We thus define a deadlock reduction criteria based on how the outgoing transitions are guarded.
+However here we want to build a refinement relation that  also guarantees that no deadlock is introduced when refining the automaton.
+This property is quite frequent in refinement relation, and referred to as \emph{lack of new deadlocks}~\cite{Kouchnarenko:2007} or \emph{complete simulation}~\cite{sangiorgi:bisim-coind12}.
+The notion of deadlock should however be specialised to our OA.
+Indeed, the possible transitions are better characterised by the guards of the outgoing transitions from a given state, rather than the simple existence of a transition.
+We thus define a deadlock reduction criterion based on how the outgoing transitions are guarded.
 As such, a refinement does not introduce deadlocks if in the conditions where no transition is possible in the refined automaton, no transition are already possible in the more general one.
-More formally, for any pair of states $s_1$ and $s_2$  we introduce a criteria of the form:
+More formally, for any pair of states $s_1$ and $s_2$  we introduce a criterion of the form:
 \[
@@
 Fig.
-\ref{Fig:SpecOA} shows the OA modelling this simpler version of the system, that we refer to as \texttt{Simprod-cons}.
+\ref{Fig:SpecOA} shows the OA modelling this simpler version of the system, that we refer to as \texttt{simprod-cons}.
 \begin{figure}[!t]
@@
    \includegraphics[width=.90\textwidth]{Figures/FIFOpen2.pdf}
-   \caption{  The \texttt{Simprod-cons} Open automaton: the system using one-place  buffer.  \label{Fig:SpecOA}}
+   \caption{  The \texttt{simprod-cons} Open automaton: the system using one-place  buffer.  \label{Fig:SpecOA}}
 \end{figure}
@@
 An automatic tool would only need to find an over approximation of reachability to reason on composition that is compatible with deadlock reduction.
-We call \emph{non-blocking composition} a composition that can be safely be used to compose OA that are involved in a deadlock reducing relation.
+We call \emph{non-blocking composition} a composition that can  safely be used to compose OA that are involved in a deadlock reducing relation.
 
@@
 It will be used to prove composition theorems in  Section~\ref{sec:prop}.
-Proving refinement relation in absence of non-blocking composition can always be done specifically for the composed automaton under study.
+Proving refinement relation in absence of non-blocking composition may also checked specifically for the composed automaton under study.
 %It is not sufficient to ensure the existence of equivalent transitions in general, but it will be sufficient in the context of refinement.
@@
 What is less classical is the definition of this relation because it is a boolean formula.
-For each couple of states  $s_1$ and $s_3$ of $A_1$ and $A_3$ we build a a formula that defines the refinement relation.
+For each couple of states  $s_1$ and $s_3$ of $A_1$ and $A_3$ we build a  formula that defines the refinement relation.
 To do this, we take the disjunction of formulas relating $s_1$ and $s_3$, and passing by all states $s_2$ of $A_2$.
@@
  refinement is compositional in the sense that it is sufficient to prove refinement for the composed automata separately to obtain a refinement relation.
-The second part,  proving that placing in the same context two OA in refinement, we obtain two OA in refinement is left for future works.
+The second part,  proving that placing in the same context two OAs in refinement, we obtain two OAs in refinement is left for future works.
 %
@@
 
-\begin{example}  Consider again the \texttt{prod-cons} and \texttt{Simprod-cons}  automata given in the examples above.
+\begin{example}  Consider again the \texttt{prod-cons} and \texttt{simprod-cons}  automata given in the examples above.
 Since  \texttt{prod-cons} $\leq_{\{\texttt{P,Q}\}}$ \texttt{simprod-cons},  then according to Theorem \ref{thm:ContextRefinement},
-\texttt{prod-cons[producer/P]} $\leq_{\{\texttt{Q}\}}$  \texttt{Simprod-cons[producer/P]}. 
+\texttt{prod-cons[producer/P]} $\leq_{\{\texttt{Q}\}}$  \texttt{simprod-cons[producer/P]}. 
 The automaton of \texttt{prod-cons[producer/P]} is shown in Fig.~\ref{Fig:ComposeOA}.
@@
 Let $A_1$, $A_2$, $A_3$ and $A_4$ be four OA with $\wrel{A_1}{A_2}{H}$ and $\wrel{A_3}{A_4}{H'}$.
-Let $J_1$ and $J_2$ be the set of holes of $A_1$ and $A_2$ resp.
-and suppose that \(k \in J_1 \cap J_2\).
-We have: \[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_4}{k}}{J_1 \uplus J_2 \uplus J_3 \uplus J_4 \uplus H \uplus H'\setminus \mbrc{k}}\]
+Suppose that \(k \in H\).
+We have: \[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_4}{k}}{ H \uplus H'\setminus \mbrc{k}}\]
 \end{theorem}
@@
 \begin{example}
-As an example of the use of this theorem, if we design a refined version of the producer process of Example~\ref{Example:prodandcons} called $\texttt{producer}^{\flat}$.
+As an example of the use of this theorem, if we design a refined version of the producer process of Example~\ref{Example:prodandcons} called $\texttt{Refproducer}$.
 According to  Theorem \ref{thm:Composability}, we have
-\texttt{prod-cons[producer/P]} $\leq_{\{\texttt{Q}\}}$  \texttt{Simprod-cons[$\texttt{producer}^{\flat}$/P]}. 
+\texttt{prod-cons[producer/P]} $\leq_{\{\texttt{Q}\}}$  \texttt{simprod-cons[$\texttt{Refproducer}$/P]}. 
 %as well as \texttt{prod-cons[P/producer]} $\leq_{\{\texttt{Q}\}}$  \texttt{Simprod-cons[P/$\texttt{producer}^{\flat}$]}.
@@
 
-\TODO{parler de generalisation a la composition a n automates}
+Note that the substitution operation can be extended to a multiple substitution that fills several holes at the same time, and the theorems can be adapted accordingly.
+
+%\TODO{parler de generalisation a la composition a n automates}
 
@@
 \cite{GayH:2005,BravettiZ:2021}.
-Such refinement is  instead based  on interface-oriented approach, it allows the expression more internal choices and less external choices.
+This kind of refinement is  based  on interface-oriented approach, it allows the expression of more internal choices and less external choices.
 The refinement of open systems is also defined in terms of  alternating simulation \cite{Alur:1998,deAlfaro:2021}, which deals with game-based models.
@@
 our approach to design refinement  has some commonalities with that of the above mentioned \cite{deAlfaro:2021}: both are process-oriented approach even if they are not based on the same notion of simulation and they are based on optimistic approach to composition.
-For the composability, we shall see that we use the notion of comparability of holes (similar to the notion of compatibility), which is explicitly encompassed in the definition of composition.
+For the composability, we use the notion of comparability of holes (similar to the notion of compatibility), which is explicitly encompassed in the definition of composition.
 
@@
 The simulation  ensures the preservation of   
-safety properties as deadlock-freeness  and, more generally, all 
+safety properties as deadlock-freeness  and, more generally, 
 all linear temporal logic properties.
-The issue is about the properties of simulation, in particular closure properties such as preservation under composition.
+Our focus is about the properties of simulation, in particular closure properties such as preservation under composition.
 Some works   have addressed the problem of non-introduction of blocking by composition.
@@
 In this article we investigated the notion of refinement for a symbolic and open model: open automata. 
-OA are convenient to model parallel systems that are parameterised both by the use of variables and by the possibility to compose automata.
+OAs are convenient to model parallel systems that are parameterised both by the use of variables and by the possibility to compose automata.
 The refinement relation first relies on a simulation relation between the specification and its refinement, but it also specifies that the refined process must follow the behaviour of the specification, not only at every compatible state but also along any trace.
@@
 \begin{center}
-\includegraphics[scale=0.7]{Figures/Thm2intuition}
+\includegraphics[scale=0.7]{Figures/Thm1intuition}
 \end{center}

### 2023-05-25 2021-Refinement/paper/refinementarticleV2.tex
reu rabea

@@
 \subsection{Preliminaries and notations}
-Families of values, or equivalently maps will be noted \(x_i^{i \in I}\), \(\mset{i \mapsto x_i}{i \in I}\), or \(\mset{i \gets x_i}{i \in I}\), depending on what is more convenient.
+Families of values, or equivalently maps will be noted \(x_i^{i \in I}\), \(\mset{i \mapsto x_i}{i \in I}\), or \(\mset{i \gets x_i}{i \in I}\), depending on what is more convenient (e.g.
+$i \gets x_i$ is used for maps that are used as substitution).
 Statements like  $\exists c_j^{j \in J}$ defines both $J$ and the mapping ${j \mapsto c_j}$.
@@
 %\begin{definition}[Expression algebra, Action algebra, Formulas, Terms]
-An expression algebra \(E\) is the disjoint union  of  terms,  actions, and  formulas
+Our expression algebra \(E\) is the disjoint union  of  terms,  actions, and  formulas
 \( E=\terms \uplus \actions \uplus \formulas\) .
@@
 %\end{definition}
-
 For \(e \in E\),
- \(\fvars{e}\) is the set of variables in  $e$ that are not bound by a binder. An expression is closed if \(\fvars{e}=\emptyset\).
+ \(\fvars{e}\) is the set of variables in  $e$ that are not bound by a binder. 
+An expression is closed if \(\fvars{e}=\emptyset\).
 The set \(\values\) denotes values which is a subset of closed terms.
@@
 the formulas such that  \(\fvars{f}\subseteq V\).
-The substitution in \(e \in E\) of \(x \in \fvars{e}\) by \(t \in \terms\), is denoted \(e\subst{t}{x}\), and its generalisation to the parallel substitution of variables in \(V\) by \(\psi: V \to \terms\) is denoted \(e\psubst{\psi}\).
-
- We suppose given a decidable satisfiability relation on formulas; we denote \({\vdash} f\) the satisfiability over closed formulas.
+%The substitution in \(e \in E\) of \(x \in \fvars{e}\) by \(t \in \terms\), is denoted \(e\subst{t}{x}\), and its generalisation to t
+The parallel substitution of variables in \(V\) by a map \(\psi: V \to \terms\) is denoted \(e\psubst{\psi}\).
+
+ We suppose given a decidable satisfiability relation on closed formulas, denoted \({\vdash} f\).
 % In practice one of our objective is to be able to use a SMT solver to reason automatically on the properties of open automata, in this case
@@
 
-\RAB{Pourquoi on parle bisimulation??}
-The bisimulation relation that we consider is the one that makes $A_1$ and $A_2$ bisimilar, complemented with identity of configurations for $A_3$.
-The proof relies on the fact that, by construction, all transitions of the composed automaton $A_1\subst{A_3}{k}$ are specified by open transitions of $A_1$.
+\begin{proofsketch}
+The proof relies on a simulation relation that we consider is the one that makes $A_1$ and $A_2$ similar, complemented with identity of configurations for $A_3$.
+Then, by construction, all transitions of the composed automaton $A_1\subst{A_3}{k}$ are specified by open transitions of $A_1$.
 For the transitions that do not involve hole $k$, the transition of $A_1\subst{A_3}{k}$ is the same and simulation between $A_1$ and $A_2$ allows us to conclude directly.
 If the hole $k$ is involved the considered relation  implies that valuations in $A_3$ are equal (i.e., the value for each variable are the same in both valuations), after a transition we should obtain ``equal'' valuations because post-conditions are deterministic.
+\end{proofsketch}
 

### 2023-06-01 2021-Refinement/paper/refinementarticleV2.tex
introduction et bib

@@
 
-Automata are convenient for specifying` and verifying systems, but most automata definitions allow only the specifications of finite closed systems.
+Automata are convenient for specifying and verifying systems, but most automata definitions allow only the specifications of finite closed systems.
 Indeed those systems are the ones we can verify efficiently, but programming often consists in writing open systems that should be interfaced with others, and with potentially unbound behaviours (at least statically).
@@
 
-Refinement relations verify that an implementation satisfies some properties with respect to a specification.
+\RAB{The refinement concept plays  an important role in software engineering.
+In addition to helping to cope with the complexity, refinement provides a foundation for ensuring  system (software) correctness.
+The correctness of a system can
+be established by proving, that a system refines its specification.}
+%Refinement relations verify that an implementation satisfies some properties with respect to a specification. 
 Refinement entails that one system  can be considered as a more precise version of the specification, featuring all the specified behaviours with more concrete details.
-In this article we mostly rely on a simulation point of view, where all the specified behaviour must be followed by the refined system but additional behaviours may exist.
-However we also ensure that a whole scenario, made of several steps, of the specification can also be simulated by the refined system, which is slightly richer than the traditional simulation relation.
-
-The notion of refinement  captures the relation between  a specification and an implementation of the same component.
-Refinement entails that one system can be considered as a more precise version of the specification, featuring all the specified behaviours with more concrete details.
- It is usually defined as trace inclusion or simulation  \cite{Milner:1980,Kouchnarenko:2007}; this ensures that all behaviours of the specification must belong to the behaviours of the implementation.
+From  formal point of view,  refinement can be defined as a mathematical relations between a specification and its implementation.
+It is usually defined as trace inclusion or simulation  \cite{Milner:1980,Kouchnarenko:2007}.
+Each  offers specific guarantees on the  behavioural properties of the specification, and it ensures that all behaviours of the specification must belong to the behaviours of the implementation.
 This definition, which is based on systems whose behaviour is fully defined, is not well-suited for open systems,  as it requires to reason also about unspecified behaviours.
@@
 It has already good properties relatively to bisimulation, but refinement relations were not studied.
-
-This article first introduces OA that were defined in  \cite{henrio:01299562}. %,  but compared to previous works, we 
-and additionaly defines the composition of OA.
-Then we define  a refinement relation for OA that has the following characteristics:
+In this article we go further to  define a theory of refinement to OA.
+The refinement relation we introduce in the paper  is based on the notion of   simulation,  in a similar way to that defined in classical automata theory \cite{Milner:1989,Bellegarde:2000}.
+And with the common behaviour-preserving  property:  all the behaviour of the abstract specification must be followed by its (complex) implementation but additional behaviours may exist.
+However we also ensure that a whole scenario, made of several steps, of the specification can also be simulated by the refined system, which is slightly richer than the traditional simulation relation and which allows us to obtain a compositionality result.
+
+%This article first introduces OA that were defined in  \cite{henrio:01299562}. %,  but compared to previous works, we and additionally defines the composition of OA.
+Our contribution in this paper is the definition a refinement relation for OA that has the following characteristics:
 \begin{itemize}
@@
 The idea is that two states are related depending on the satisfiability of the expression relying their variables i.e., if the variables of the OA verify a certain formula. 
-In other words, to each pair of states is attached a boolean formula that may refer to the  variables of each of the two OAs, stating whether the two states are related or not.
+In other words, to each pair of states is attached a boolean formula that may refer to the  variables of each of the two OA, stating whether the two states are related or not.
 Additionally, we may check that initial states of the automata are related by checking that: \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\).
@@
 We can then define a configuration relation $R$ such that $R(s,s_2)$ is true and $R(t,t_2)$ holds when $z\geq 0$ and $y=z$, while $R(t',t_2)$ holds when $z< 0$ and $y=-z$.
-This illustrates relation on configuration, but also allows us to realise that bisimulation on OAs is a bit more complex than in the classical case.
+This illustrates relation on configuration, but also allows us to realise that bisimulation on OA is a bit more complex than in the classical case.
 Indeed, we need two transitions on the left OA to simulate a single transition on the right one.
@@
  Then 
-$\mathcal{R}$, a relation on configurations of OAs, is an FH-bisimulation if and only if for any  states
+$\mathcal{R}$, a relation on configurations of OA, is an FH-bisimulation if and only if for any  states
 $s\in{S}_1$ and $t\in{S}_2$, we 
@@
 %Finally, we should take into account that 1) instead of equality, we should check if there is a state such that both transitions are feasible (the conjunction of guards is satisfiable), and that  2) instead of finding another transition of the specification we might find a family of transitions that cover all the cases of the transition of the implementation.
-We can now state the definition of simulation between OAs that have the same set of holes.
+We can now state the definition of simulation between OA that have the same set of holes.
 
@@
  refinement is compositional in the sense that it is sufficient to prove refinement for the composed automata separately to obtain a refinement relation.
-The second part,  proving that placing in the same context two OAs in refinement, we obtain two OAs in refinement is left for future works.
+The second part,  proving that placing in the same context two OA in refinement, we obtain two OA in refinement is left for future works.
 %
@@
 In this article we investigated the notion of refinement for a symbolic and open model: open automata. 
-OAs are convenient to model parallel systems that are parameterised both by the use of variables and by the possibility to compose automata.
+OA are convenient to model parallel systems that are parameterised both by the use of variables and by the possibility to compose automata.
 The refinement relation first relies on a simulation relation between the specification and its refinement, but it also specifies that the refined process must follow the behaviour of the specification, not only at every compatible state but also along any trace.

### 2023-06-02 2021-Refinement/paper/refinementarticleV2.tex
introd...

@@
 
-The following of this article is organised as follows. 
-Section~\ref{sec:background} recalls the definition of open automata and defines their composition. 
+This paper is organized as follows. Section~\ref{sec:background} recalls the definition of OA and defines their composition. 
 We  then  define a refinement relation for OA, first only considering two automata with the same set of holes in Section~\ref{sec:refinement} and generalize it to automata with a different set of holes in Section~\ref{sec:holes}.
-Section~\ref{sec:prop} is dedicated to formalize and prove basic properties of refinement in ; here we prove that refinement is a preorder and has good composition property.
+Section~\ref{sec:prop} is dedicated to formalize and prove basic properties of the refinement defined  ; here we prove that refinement is a preorder and has nice composability properties.
 In Section~\ref{sec:sota} we review related works, and Section~\ref{sec:ccl} concludes the paper.
@@
    \includegraphics[width=.99\textwidth]{Figures/FIFORing.pdf}
-   \caption{Open automaton for the \texttt{prod-cons} system using FIFO circular buffer.
+   \caption{OA for the \texttt{prod-cons} system using FIFO circular buffer.
     \label{Fig:RefineOA}} 
@@
 
-\paragraph{Open automaton composition.}
+\paragraph{Open automata composition.}
 
@@
    \includegraphics[width=.99\textwidth]{Figures/compos-FIFO-Pro.pdf}
-   \caption{Open automaton for \texttt{prod-cons}[\texttt{P}/\texttt{producer}]. 
+   \caption{OA for \texttt{prod-cons}[\texttt{P}/\texttt{producer}]. 
    \label{Fig:ComposeOA}} 
@@
    \includegraphics[width=.90\textwidth]{Figures/FIFOpen2.pdf}
-   \caption{  The \texttt{simprod-cons} Open automaton: the system using one-place  buffer.  \label{Fig:SpecOA}}
+   \caption{  The \texttt{simprod-cons} OA: the system using one-place  buffer.  \label{Fig:SpecOA}}
 \end{figure}

### 2023-06-02 2021-Refinement/paper/refinementarticleV2.tex
refs

@@
 This section presents our notations and the principles of automata.
-Except for minor changes in the notations, compared to previous works~\cite{fhbisim} the only new contribution is the definition of a composition operator for OA.
+Except for minor changes in the notations, compared to previous works~\cite{AMHEEMA:2023} the only new contribution is the definition of a composition operator for OA.
 %
@@
 The automaton has a single state with  two holes: $\texttt{P}$ and  $\texttt{Q}$ that are the two interacting processes.
-$\texttt{l}$   indicates the next available position for  enqueuing an element  and  $\texttt{f}$ is the position that contains the next element to be dequeued.
+$\texttt{l}$ (as last)  indicates the next available position for  enqueuing an element  and  $\texttt{f}$ (as first) is the position that contains the next element to be dequeued.
 %\footnote{The  arrow  without any state of origin is a graphical convention to indicate that the pointers are initialized at the beginning}.
@@
 
-Bisimulation between OA was defined in~\cite{fhbisim}.  We show below the principles of this bisimulation. We first recall the usual definition of bisimulation.
+Bisimulation between OA was defined in~\cite{AMHEEMA:2023}.  We show below the principles of this bisimulation. We first recall the usual definition of bisimulation.
 Bisimulation can  be defined as follows for standard transition systems:
@@
 We should check that these two transitions cover all the cases accepted by the right hand side OA, and of course that destination states are in relation.
-Formally, FH-bisimulation is defined \cite{fhbisim} as follows:
+Formally, FH-bisimulation is defined \cite{AMHEEMA:2023} as follows:
 
@@
 
-Similarly to FH-bisimulation~\cite{fhbisim} we are interested  in finding refinement relations between configurations of two OA that contain variables and holes.
+Similarly to FH-bisimulation~\cite{AMHEEMA:2023} we are interested  in finding refinement relations between configurations of two OA that contain variables and holes.
 When dealing with open systems it is common to define refinement in terms of a simulation relation.
@@
 Previous works on OA focused on equivalence relations compatible with composition.
-In  \cite{10.1145/3372884.3373161}, a computable bisimulation is introduced, while in \cite{fhbisim} is introduced a weak version of the bisimulation on OA. 
+In  \cite{10.1145/3372884.3373161}, a computable bisimulation is introduced, while in \cite{AMHEEMA:2023} is introduced a weak version of the bisimulation on OA. 
 In this paper we tackle the refinement relation in the form of simulation, as is the case for the corresponding relations on labelled transition systems \cite{10.1007/3-540-46428-X_19}.

### 2023-06-07 2021-Refinement/paper/refinementarticleV2.tex
intro + concl

@@
 
-* open automata  / Open Automata -> only use open automata or OA.
+* \st{open automata  / Open Automata -> only use open automata or OA.}
 
@@
 
-Automata are convenient for specifying and verifying systems, but most automata definitions allow only the specifications of finite closed systems.
+The present trend in software engineering is towards component-based design. Compositional design is a highly convenient approach 
+for specifying and verifying large systems.
+Automata are the basic formalism for this approach, but most automata definitions allow only the specifications of finite closed systems.
 Indeed those systems are the ones we can verify efficiently, but programming often consists in writing open systems that should be interfaced with others, and with potentially unbound behaviours (at least statically).
@@
 
+There are research work
+Various other papers have considered the relationship b
 There are some works that have focused on  the refinement of open systems. Defining refinement of open systems as trace inclusion  is  addressed  as a notion of subtyping in type theory 
@@
 In this article we investigated the notion of refinement for a symbolic and open model: open automata. 
-OA are convenient to model parallel systems that are parameterised both by the use of variables and by the possibility to compose automata.
+OA are convenient for component-based software design.
+Indeed, OA allow the designer to model parallel systems that are parameterised both by the use of variables and by the possibility to compose automata.
+The formalism supports compositional specification through the refinement paradigm.
+The contribution of this paper...
 The refinement relation first relies on a simulation relation between the specification and its refinement, but it also specifies that the refined process must follow the behaviour of the specification, not only at every compatible state but also along any trace.

### 2023-06-13 2021-Refinement/paper/refinementarticleV2.tex
visio

@@
 
-We define several variants of refinement relations between systems including either equal or different sets of holes, and 
+We define refinement relations between systems including either equal or different sets of holes, and 
 show under which conditions these refinements are preserved by composition of open automata.
@@
 \section{Introduction}
-
-\TODO{TODO list}
-
-* \st{example a terminer}
-
-* choisir terminologie: refinement or simulation
-
-* \st{open automata  / Open Automata -> only use open automata or OA.}
-
-* positioning
-
-* \st{format according to conf: lncs FACS or SEFM}
-
-* global rewriting (partly done)
-
+%
+%
+%\TODO{TODO list}
+%
+%
+%* \st{example a terminer}
+%
+%* choisir terminologie: refinement or simulation
+%
+%* \st{open automata  / Open Automata -> only use open automata or OA.}
+%
+%* positioning
+%
+%* \st{format according to conf: lncs FACS or SEFM}
+%
+%* global rewriting (partly done)
+
+\TODO{intro}
 The present trend in software engineering is towards component-based design. Compositional design is a highly convenient approach 
@@
 \end{example}
-\TODO{potential ex 4: check if the example with a hole filled is a simulation of the example with holes? at least state \texttt{prod-cons} $\leq_{\{\texttt{P,Q}\}}$ \texttt{simprod-cons}}
+%\TODO{potential ex 4: check if the example with a hole filled is a simulation of the example with holes? }
 
@@
 
-Consequently, as the simulation is transitive \TODO{TODO Thm 4}
-We can state the following theorem: 
+Consequently, as the simulation is transitive we can compose the previous theorems and  state the following: 
 \begin{theorem}[Composability]\label{thm:Composability}

### 2023-06-16 2021-Refinement/paper/refinementarticleV2.tex
correction mineure..
Refinement...

@@
 Our expression algebra \(E\) is the disjoint union  of  terms,  actions, and  formulas
-\( E=\terms \uplus \actions \uplus \formulas\) .
+\( E=\terms \uplus \actions \uplus \formulas\).
 \(\terms\) and \(\actions\) are term algebras.
@@
 
-There are research work
-Various other papers have considered the relationship b
-There are some works that have focused on  the refinement of open systems. Defining refinement of open systems as trace inclusion  is  addressed  as a notion of subtyping in type theory 
+The origins of the refinement are in the  approach of programming that aims to provide solid foundations for building correct programs \cite{Dijkstra76}.
+There many work that contributed to the further development of the refinement calculus in various area (e.g.
+\cite{BACK1990133,Abrialbooks96,soton250550,Bellegarde:2000}).
+However, the work focused on the analysis and applicability of refinement to systems that are inherently closed, i.e., systems which is bounded and without environment,
+
+There is not a lot of works that has focused on  the refinement of open systems. Defining refinement of open systems as trace inclusion  is  addressed  as a notion of subtyping in type theory 
 \cite{GayH:2005,BravettiZ:2021}.
@@
 In  \cite{10.1145/3372884.3373161}, a computable bisimulation is introduced, while in \cite{AMHEEMA:2023} is introduced a weak version of the bisimulation on OA. 
-In this paper we tackle the refinement relation in the form of simulation, as is the case for the corresponding relations on labelled transition systems \cite{10.1007/3-540-46428-X_19}.
+In this paper we tackle the refinement relation in the form of simulation, as is the case for the corresponding relations on labelled transition systems \cite{Bellegarde:2000}.
 But unlike the standard simulation we deal with symbolic and open models.
@@
 The formalism supports compositional specification through the refinement paradigm.
-The contribution of this paper...
-The refinement relation first relies on a simulation relation between the specification and its refinement, but it also specifies that the refined process must follow the behaviour of the specification, not only at every compatible state but also along any trace.
+The contribution of this paper, we introduce refinement  between open automata.
+The refinement relation  relies on a simulation relation between the specification and its implementation;  it  specifies that the refined process must follow the behaviour of the specification, not only at every compatible state but also along any trace.
 We finally showed that refinement is a preorder that is preserved when filling a hole.

### 2023-06-19 2021-Refinement/paper/refinementarticleV2.tex
relecture sec 1 et 2

@@
 %* global rewriting (partly done)
-
-\TODO{intro}
-The present trend in software engineering is towards component-based design. Compositional design is a highly convenient approach 
+ Compositional design is a highly convenient approach 
 for specifying and verifying large systems. 
-Automata are the basic formalism for this approach, but most automata definitions allow only the specifications of finite closed systems.
+Automata are often used as the basic formalism for this approach, but most automata definitions allow only the specifications of finite closed systems.
 Indeed those systems are the ones we can verify efficiently, but programming often consists in writing open systems that should be interfaced with others, and with potentially unbound behaviours (at least statically).
@@
 
-\RAB{The refinement concept plays  an important role in software engineering.
-In addition to helping to cope with the complexity, refinement provides a foundation for ensuring  system (software) correctness.
+The refinement concept also plays  an important role in software engineering.
+In addition to helping to cope with the complexity \LUDO{of what?}, refinement provides a foundation for ensuring  system (software) correctness.
 The correctness of a system can
-be established by proving, that a system refines its specification.}
+be established by proving, that a system refines its specification.
 %Refinement relations verify that an implementation satisfies some properties with respect to a specification. 
-Refinement entails that one system  can be considered as a more precise version of the specification, featuring all the specified behaviours with more concrete details.
-From  formal point of view,  refinement can be defined as a mathematical relations between a specification and its implementation.
-It is usually defined as trace inclusion or simulation  \cite{Milner:1980,Kouchnarenko:2007}.
-Each  offers specific guarantees on the  behavioural properties of the specification, and it ensures that all behaviours of the specification must belong to the behaviours of the implementation.
-This definition, which is based on systems whose behaviour is fully defined, is not well-suited for open systems,  as it requires to reason also about unspecified behaviours.
-
-Open automata (that we abbreviate OA) were defined as a way to provide a semantics for open parameterized hierarchical LTSs used in verification tools and called \emph{pNets}.
-An OA \cite{henrio:01299562} is a classical automaton with variables and holes.
+Refinement entails that one system  can be considered as a more precise version of another one that is considered to be the specification.
+The refined model features all the specified behaviours with more concrete details.
+From a formal point of view,  refinement can be defined as a mathematical relations between a specification and its implementation, one frequently used relation is trace inclusion or simulation  \cite{Milner:1980,Kouchnarenko:2007}.
+Each \LUDO{each what?} offers specific guarantees on the  behavioural properties of the specification, and it \LUDO{what is ``it''?} ensures that all behaviours of the specification must belong to the behaviours of the implementation.
+This definition \LUDO{which definition?}, which is based on systems whose behaviour is fully defined, is not well-suited for open systems,  as it requires to reason also about unspecified behaviours.
+
+Open automata (that we abbreviate OA) were defined as a way to provide a semantics for open parameterized hierarchical labelled transition systems (abbreviated LTS).
+They were proposed as a theoretical foundation for parametrised automatas used in verification tools and called \emph{pNets}.
+An OA \cite{henrio:01299562} is similar to a classical automaton but with variables and holes.
 Variables make automata symbolic and allow them to encode infinite state systems.
-Holes enable the composition of automata: an automaton with a hole is an operator that takes another automaton as parameter and reacts to the actions it emits; the composed automaton is a more precise automaton where the behaviour of one ``process parameter'' % \TODO{est-ce qu'on n'ecrirait pas ici "process parameter" pour les distinguer des variables standard ?}
-% LUDO: DONE
+Holes enable the composition of automata: an automaton with a hole is an operator that takes another automaton as parameter and reacts to the actions it emits; the composed automaton is an automaton where the behaviour of one ``process parameter'' %
  of the main automaton has been provided.
@@
 \item Classical simulation characterisation but also an additional criteria ensuring that refinement does not introduce deadlocks when following a trace from the simulated automaton.
-\item Good properties relatively to composition: we prove here that filling the same hole  with the same automaton preserves the refinement relation.
+\item Good properties relatively to composition: we prove that composition preserves the refinement relation.
 \item Ability to take into account both composition and transitivity: this is a challenge because composition changes the set of holes of the OA and refinement takes into account the actions of the holes.
@@
 \subsection{Preliminaries and notations}
-Families of values, or equivalently maps will be noted \(x_i^{i \in I}\), \(\mset{i \mapsto x_i}{i \in I}\), or \(\mset{i \gets x_i}{i \in I}\), depending on what is more convenient (e.g.
+Families of values (equivalent to maps) will be noted \(x_i^{i \in I}\), \(\mset{i \mapsto x_i}{i \in I}\), or \(\mset{i \gets x_i}{i \in I}\), depending on what is more convenient (e.g.
 $i \gets x_i$ is used for maps that are used as substitution).
@@
 \end{definition}
-
+A pair consisting of a state and a valuation is called a \emph{configuration} (of the automaton).
 We use two operators to access pieces of information of the OA.
@@
 \begin{definition}[Out-transition, Transition variables]
-Let \(V\) be the variable names of the considered automaton, \(T\) its transitions and \(r\) one of its states.
+Let \(V\) be the variable names of a considered automaton, \(T\) its transitions and \(r\) one of its states.
 \(\fOT[T]{r} \subset T\) are called the out-transitions of the state \(r\).
 %\(\fIT[T]{r} \subset T\) are called the in-transitions of the state \(r\).
-When the transition set is clear from the context, it will be omitted.
+When the set \(T\) is clear from the context, it will be omitted.
 The local variables of a transition \(\fvars{t}\) are all variables appearing in transition \(t\) except the variables of the automaton.
@@
 
-A pair consisting of a state and a valuation is called a \emph{configuration}.
 %
@@
 The example uses several kinds of data.
-Variable $\texttt{m}$ holds a message, message types do not need a concrete definition here.
+Variable $\texttt{m}$ holds a message (we can leave the message type abstract here).
 We additionally use arrays of messages with a syntax of the form $\texttt{M[l]}$ for array accesses; $\texttt{M}$ is an array of $\texttt{N}$ elements, from $0$ to $\texttt{N}-1$.
@@
 The plugging operation is called composition.
-The composition of OA was already implicitly defined by the means of composition on pNets in previous work \cite{henrio:01299562} but never  formalised on OA.\footnote{The definition of composition below is a direct translation of what happens with pNets composition \cite{henrio:01299562} without  introducing pNets.}
+The composition of OA was already implicitly defined by the means of composition on pNets in previous work \cite{henrio:01299562}. We provide here a (new) direct definition of composition for OA.
 
@@
 \ref{Fig:procandcons} shows a producer automaton  and a consumer  automaton that can be used  to fill the holes $\texttt{P}$ and $\texttt{Q}$ of \texttt{prod-cons} defined in Example~\ref{Example:fifo-system}.
- \begin{figure}[!ht]
+ \begin{figure}[!b]
  \centering
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!b]
  \centering
@@
 \begin{definition}[Relation on open automata configurations] Suppose $V_1$ and $V_2$ are disjoint.
-A relation on configurations of two OA \(\OAg[1]\) and \(\OAg[2]\) is a function \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
+A relation on configurations of two OA \(\OAg[1]\) and \(\OAg[2]\) is a function \( \mathcal{R}: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\).
 \end{definition}
@@
 In other words, to each pair of states is attached a boolean formula that may refer to the  variables of each of the two OA, stating whether the two states are related or not.
-Additionally, we may check that initial states of the automata are related by checking that: \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\).
+Additionally, we say that the relation $ \mathcal{R}$ \emph{relates the initial states} of the automata if: \(\sigma_{01} \uplus \sigma_{02} \vdash  \mathcal{R}\mpar{s_{01}, s_{02}}\).
 
@@
 
+Two automata are bisimilar if there exists a strong FH-bisimulation $ \mathcal{R}$ that relates their initial states.
+
 % \TODO{Eric: il reste des petits bugs genre $s^{2'}_x$ plutot que

### 2023-06-19 2021-Refinement/paper/refinementarticleV2.tex
sec 2

@@
 \begin{definition}[Classical Bisimulation]
-  A bisimulation is a relation $\mathcal{R}$ such that $s~\mathcal{R}~t$:\\
+  A bisimulation is a relation $\mathcal{R}$ such that if $s~\mathcal{R}~t$ then:\\
   \begin{minipage}[c]{.6\textwidth}
@@
     \]
-    \begin{center}
+\begin{center}    \vspace{-1.5ex}
       and conversely
@@
   \end{minipage}
-$s$ and $t$ are bisimilar, written $s\sim t$ iff there is a bisimulation relation $R$ such that  $s ~\mathcal{R}~ t$
+$s$ and $t$ are bisimilar, written $s\sim t$ iff there is a bisimulation relation $\mathcal{R}$ such that  $s ~\mathcal{R}~ t$
 \end{definition}
@@
 A  bisimulation relation  relates pair of states and ensures that any behaviour of one automaton can be performed by the other one while staying in relation.
-We informally explain here the symbolic nature of the bisimulation and the related complexity of its definition.
-The presence of holes in fact raises no strong difficulty here.
+We informally explain here the symbolic nature of the bisimulation for OA and the related complexity of its definition.
+The presence of holes in fact raises no strong difficulty but the variables must be handled carefully.
 Consider the two following simple OA:
@@
 
-We would like these two OA to be considered bisimilar. Both can input any $\beta(x)$ input on their hole and stores the value of $x$, emitting $\alpha(x)$ along the transition.
+We should be able to consider these two OA as bisimilar. Both can input any $\beta(x)$ input on their hole and stores the value of $x$, emitting $\alpha(x)$ along the transition.
 The difference is the way $x$ is stored.
-We can then define a configuration relation $R$ such that $R(s,s_2)$ is true and $R(t,t_2)$ holds when $z\geq 0$ and $y=z$, while $R(t',t_2)$ holds when $z< 0$ and $y=-z$.
-This illustrates relation on configuration, but also allows us to realise that bisimulation on OA is a bit more complex than in the classical case.
-Indeed, we need two transitions on the left OA to simulate a single transition on the right one.
+We can then define a configuration relation $\mathcal{R}$ such that $\mathcal{R}(s,s_2)$ is true and $\mathcal{R}(t,t_2)$ holds when $z\geq 0$ and $y=z$, while $\mathcal{R}(t',t_2)$ holds when $z< 0$ and $y=-z$.
+This illustrates relation on configurations, but also shows that bisimulation on OA is more complex than in the classical case.
+Indeed, we need two transitions on the left OA to simulate a single one on the right OA.
 We should check that these two transitions cover all the cases accepted by the right hand side OA, and of course that destination states are in relation.
-Formally, FH-bisimulation is defined \cite{AMHEEMA:2023} as follows:
+Formally, FH-bisimulation is defined as follows \cite{AMHEEMA:2023}:
 
@@
  \end{definition}
-Note in this definition, instead of matching an instantiated transition  of the first automata to another instantiated transition of the second, it matches an open transition $t_1$ to a family of covering open transitions $t_{2x}^{x\in X}$.
-Technically, the following sections do not rely on the definition of strong bisimulation on OA, but they follow the same principles and in particular the same way to faithfully simulate an open transition by a set of other open transitions.
+Note that this definition matches an open transition $t_1$ to a family of covering open transitions $t_{2x}^{x\in X}$.
 Intuitively, this means that for every pair of related
 states $(s_1,s_2)$  of the two automata, and for every  transition of the first automaton from $s_1$, there is a set of matching transitions  of the second automaton  from $s_2$ such that the produced action match, the actions of the same holes and the successors are related after variable update.
+Technically, the following sections do not rely on the definition of strong bisimulation on OA, but they follow the same principles and in particular the same way to faithfully simulate an open transition by a set of other open transitions.
 
@@
 \subsection{Reachability}
-We finally define a predicate abstracting state reachability for OA, it  allows us to reason on reachable states in an automaton.
-It can alternatively be seen as an abstraction of the reachable states under the form of a predicate that must stay verified along the execution of the OA.
+We finally define a new predicate abstracting state reachability for OA, it  allows us to reason on reachable states in an automaton.
+It can  be seen as an abstraction of the reachable states under the form of a predicate that must stay verified along the execution of the OA.
 \begin{definition}[Reachability] \label{Def:Reach}

### 2023-06-19 2021-Refinement/paper/refinementarticleV2.tex
coherence notations

@@
 It has already good properties relatively to bisimulation, but refinement relations were not studied.
-In this article we go further to  define a theory of refinement to OA.
-The refinement relation we introduce in the paper  is based on the notion of   simulation,  in a similar way to that defined in classical automata theory \cite{Milner:1989,Bellegarde:2000}.
+In this article we go further to  define a theory of simulation for OA.
+The simulation relation we introduce in the paper  is based on the notion of   simulation,  in a similar way to that defined in classical automata theory \cite{Milner:1989,Bellegarde:2000}.
 And with the common behaviour-preserving  property:  all the behaviour of the abstract specification must be followed by its (complex) implementation but additional behaviours may exist.
@@
 %This article first introduces OA that were defined in  \cite{henrio:01299562}. %,  but compared to previous works, we and additionally defines the composition of OA.
-Our contribution in this paper is the definition a refinement relation for OA that has the following characteristics:
+Our contribution in this paper is the definition a simulation relation for OA that has the following characteristics:
 \begin{itemize}
-\item Classical simulation characterisation but also an additional criteria ensuring that refinement does not introduce deadlocks when following a trace from the simulated automaton.
-\item Good properties relatively to composition: we prove that composition preserves the refinement relation.
-\item Ability to take into account both composition and transitivity: this is a challenge because composition changes the set of holes of the OA and refinement takes into account the actions of the holes.
+\item Classical simulation characterisation but also an additional criteria ensuring that simulation does not introduce deadlocks when following a trace from the simulated automaton.
+\item Good properties relatively to composition: we prove that composition preserves the simulation relation.
+\item Ability to take into account both composition and transitivity: this is a challenge because composition changes the set of holes of the OA and simulation takes into account the actions of the holes.
 \end{itemize}
- The refinement relation is introduced in two steps.
-First we define a refinement that relates two automata with the same holes, which allows us to focus on the automaton aspect.
+ The simulation relation is introduced in two steps.
+First we define a simulation that relates two automata with the same holes, which allows us to focus on the automaton aspect.
 Second we introduce a relation that relates two automata with different sets of holes, which allows us to take into account the open nature of OA, and to deal with composition.
-Properties of the refinement are stated and proven on the second, more general version of the relation, they are thus also valid for the first simpler refinement relation.
+Properties of the simulation are stated and proven on the second, more general version of the relation, they are thus also valid for the first simpler simulation relation.
 
 This paper is organized as follows. Section~\ref{sec:background} recalls the definition of OA and defines their composition. 
-We  then  define a refinement relation for OA, first only considering two automata with the same set of holes in Section~\ref{sec:refinement} and generalize it to automata with a different set of holes in Section~\ref{sec:holes}.
-Section~\ref{sec:prop} is dedicated to formalize and prove basic properties of the refinement defined  ; here we prove that refinement is a preorder and has nice composability properties.
+We  then  define a simulation relation for OA, first only considering two automata with the same set of holes in Section~\ref{sec:refinement} and generalize it to automata with a different set of holes in Section~\ref{sec:holes}.
+Section~\ref{sec:prop} is dedicated to formalize and prove basic properties of the simulation defined; here we prove that simulation is a preorder and has nice composability properties.
 In Section~\ref{sec:sota} we review related works, and Section~\ref{sec:ccl} concludes the paper.
@@
 \subsection{Relations between open automata}
-Establishing semantic equivalences and refinement relations between different OA requires  to compare their states.
+Establishing semantic equivalences and simulation relations between different OA requires  to compare their states.
 For this purpose, we suppose that the variables of the two OA are disjoint (a renaming of variables may have to be applied before comparing OA states).
@@
 
-\section{Refinement Relations for automata with the same holes}\label{sec:refinement}
-
-Similarly to FH-bisimulation~\cite{AMHEEMA:2023} we are interested  in finding refinement relations between configurations of two OA that contain variables and holes.
-When dealing with open systems it is common to define refinement in terms of a simulation relation.
+\section{Simulation Relations for automata with the same holes}\label{sec:refinement}
+
+Similarly to FH-bisimulation~\cite{AMHEEMA:2023} we are interested  in finding simulation relations between configurations of two OA that contain variables and holes.
+When dealing with open systems it is common to define simulation in terms of a simulation relation.
 We rely on a classical notion of simulation inspired from~\cite{AMHEEMA:2023}.
-The idea is that two configurations related by a relation; if one state can do a transition, then the other can do a transition too.
-Like for bisimulation, a refinement relation characterises when two states are related, and this  characterisation is expressed as a predicate on the variables of the two automata.
-Refinement defines conditions on a predicate $R$ such that $R\mpar{s_1, s_2}$ is a predicate (possibly involving variables of the automata) that is true when the state $s_1$ of $A_1$ refines the state $s_2$ of $A_2$.
+The idea is to consider two configurations related by a relation; if one state can do a transition, then the other can do a transition too.
+Like for bisimulation, a simulation relation characterises when two states are related, and this  characterisation is expressed as a predicate on the variables of the two automata.
+Simulation defines conditions on a predicate $\mathcal{R}$ such that $\mathcal{R}\mpar{s_1, s_2}$ is a predicate (possibly involving variables of the automata) that is true when the state $s_1$ of $A_1$ refines the state $s_2$ of $A_2$.
 
@@
 
-However here we want to build a refinement relation that  also guarantees that no deadlock is introduced when refining the automaton.
-This property is quite frequent in refinement relation, and referred to as \emph{lack of new deadlocks}~\cite{Kouchnarenko:2007} or \emph{complete simulation}~\cite{sangiorgi:bisim-coind12}.
+However here we want to build a simulation relation that  also guarantees that no deadlock is introduced when refining the automaton.
+This property is quite frequent in simulation relation, and referred to as \emph{lack of new deadlocks}~\cite{Kouchnarenko:2007} or \emph{complete simulation}~\cite{sangiorgi:bisim-coind12}.
 The notion of deadlock should however be specialised to our OA.
@@
 We thus define a deadlock reduction criterion based on how the outgoing transitions are guarded.
-As such, a refinement does not introduce deadlocks if in the conditions where no transition is possible in the refined automaton, no transition are already possible in the more general one.
+As such, a simulation does not introduce deadlocks if in the conditions where no transition is possible in the refined automaton, no transition were already possible in the more general one.
 More formally, for any pair of states $s_1$ and $s_2$  we introduce a criterion of the form:
 \[
-\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \wedge \lnot( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )\implies \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
+\forall \mpar{s_1, s_2} \!\in\!
+S_1 \!\times\!
+S_2, V_1 \uplus V_2  \vdash \mathcal{R}\mpar{s_1, s_2} \wedge \lnot( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )\implies \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
 \]
@@
 \[
-\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
+\forall \mpar{s_1, s_2} \!\in\!
+S_1 \!\times\!
+S_2, V_1 \uplus V_2  \vdash \mathcal{R}\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
 \]
 
-Both statements being equivalent and one of them may reveal more intuitive than the other in different conditions, we will use them interchangeably.
+Both statements being equivalent, as each of them may reveal more intuitive than the other in different situations, we  use them interchangeably.
 %Let us first explain the reasons why simulation can introduce allow undesired behaviours to emerge and how we want to limit them. 
@@
 \begin{definition}[Hole-equal simulation]\label{def:HoleEqualSim}
-Consider two OA with identical set of holes:  \(\OAg[1]\) and \(\OAg[2]\) where  \(J_1 = J_2\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $S_1$ to $S_2$ if the following conditions hold (we could denote it $A_1\leq A_2$):
-\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
+Consider two OA with identical set of holes:  \(A_1=\OAg[1]\) and \(A_2=\OAg[2]\) where  \(J_1 = J_2\), the relation on configurations \(\mathcal{R}: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $A_1$ to $A_2$ if the following conditions hold :
+\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash \mathcal{R}\mpar{s_{01}, s_{02}}\)
 \item[(2)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)\vspace{-8pt}
@@
 }^{x \in X}\in \fOT{s_2}.\,~~\\ 
-\everymath{\displaystyle}\begin{array}{l}
+%\everymath{\displaystyle}\begin{array}{l}
 V_1 \uplus V_2 \uplus  \fvars{t_1} \uplus \bigcup_x\fvars{t_{2x}}  \vdash \hspace{7cm}
 \\
- R\mpar{s_1, s_2} \wedge g_1 \implies
+ \mathcal{R}\mpar{s_1, s_2} \wedge g_1 \implies
  \operatorname*{\bigsymb{\bigvee}}_{x \in X}
+{\everymath{\displaystyle}
 \mpar{\begin{array}{l}
 			\alpha_{2x} = \alpha_{1} \wedge \bigwedge_\subbox{j \in J} \beta_{2xj} = \beta_{1j} \nwedge\\[12pt]
-			 g_{2x} \wedge R\mpar{ s'_{1},s'_{2x}}\psubst{\psi_{2x} \uplus \psi_{1}}
-		\end{array}} 
-\end{array} 
+			 g_{2x} \wedge\mathcal{R}\mpar{ s'_{1},s'_{2x}}\psubst{\psi_{2x} \uplus \psi_{1}}
+		\end{array}} }
+%\end{array} 
 \end{multline*}
@@
 \[
-\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
+\forall \mpar{s_1, s_2} \!\in\!
+S_1 \!\times\!
+S_2, V_1 \uplus V_2  \!\vdash\!
+\mathcal{R}\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
 \]
-
+If there is a hole equal simulation from $A_1$ to $A_2$, then we say that  $A_2$ simulates $A_1$; we  denote it $A_2\leq A_1$
 \end{definition}
@@
 The first and second conditions coincide with the natural way to prove inductively that an automaton simulates another by starting with the initial state.
-The third condition ensures that the refinement relation prevents the introduction of deadlocks.
-Our definition captures a simple kind of sub-classing of OA with the same holes. It is more expressive than a strict simulation since it matches a transition with a family of transitions. 
-With such a relation we are able to check the refinement between two OA with the same level of abstraction but specified differently, for example, by duplicating states, removing transitions,  reinforcing  guards, modifying variables, etc.
-We will show in Section~\ref{sec:prop} that this refinement relation has good properties in terms of transitivity, compositionality, and reflexivity.
+The third condition ensures that  simulation  prevents the introduction of deadlocks.
+Our definition captures a simple simulation for OA with the same holes that is more expressive than a strict simulation since it matches a transition with a family of transitions. 
+For example,
+With such a relation we are able to check the simulation between two OA that differ by duplicated states, removed duplicated transitions,  reinforced  guards, different variables, etc.
+We will show in Section~\ref{sec:prop} that this simulation relation has good properties in terms of transitivity, compositionality, and reflexivity.
 
@@
 \begin{example} \label{example:fifo-system-one}
-To illustrate the refinement simulation of OA, we consider a variation on the \texttt{prod-cons} example.
+To illustrate the simulation simulation of OA, we consider a variation on the \texttt{prod-cons} example.
 Namely,  we suppose that  the two processes  \texttt{P} and  \texttt{Q} communicate through a one-place  buffer.
@@
 \ref{Fig:SpecOA} shows the OA modelling this simpler version of the system, that we refer to as \texttt{simprod-cons}.
-\begin{figure}[!t]
+\begin{figure}[!b]
  \centering
@@
 We can easily check that this automaton simulates the one of Fig.~\ref{Fig:RefineOA}.
-Indeed, one can see that  $R=\{(r_0,s_0) \mapsto \texttt{l}=\texttt{f}, (r_0,s_1) \mapsto \texttt{f}=\texttt{l}+1\% \texttt{N} \}$ is  a candidate simulation 
+Indeed, one can see that  $\mathcal{R}=\{(r_0,s_0) \mapsto \texttt{l}=\texttt{f}, (r_0,s_1) \mapsto \texttt{f}=\texttt{l}+1\% \texttt{N} \}$ is  a candidate simulation 
 relation. It follows that  \texttt{prod-cons} $\leq$ \texttt{simprod-cons}. \qed
@@
 
-The refinement relation defined above is insufficient in the setting of composition which is the main advantage of the OA-based approach.
+The simulation relation defined above is insufficient in the setting of composition which is the main advantage of the OA-based approach.
 Indeed, it should be possible to refine an automaton by filling its hole, providing a concrete view of a part of the application that was not specified originally.
@@
 However, filling holes can result in a system with more or less holes than the original system because the plugged subsystem can contain itself many holes.
-Next section  defines  a more powerful refinement relation able to reason on automata with different sets of holes.
+Next section  defines  a more powerful simulation relation able to reason on automata with different sets of holes.
 
@@
 
-\section{A Refinement Relation that Takes Holes into Account}\label{sec:holes}
+\section{A Simulation Relation that Takes Holes into Account}\label{sec:holes}
 
 This section  extends the preceding relation to automata where the set of holes is not the same.
-Indeed, when composing the set of  holes changes, and for example we want to state whether the automaton after composition is a refinement of the original automaton or not.
+Indeed, when composing the set of  holes changes, and for example we want to state whether the automaton after composition is a simulation of the original automaton or not.
 
@@
 
-Unfortunately, the deadlock reduction property in the definition of refinement is not compositional: the composition operator can itself introduce a deadlock.
+Unfortunately, the deadlock reduction property in the definition of simulation is not compositional: the composition operator can itself introduce a deadlock.
 In other words, when filling the hole of two related automata with a third one, even if there is a deadlock reduction between the two original automata, there might not be a deadlock reduction in the composed ones.
@@
 \end{definition}
-Like in the definition of refinement (Definition~\ref{def:HoleEqualSim}) we use guards to ensure that the transition can occur. 
-In general, one would not want to only consider non-blocking composition as it may reveal a bit restrictive, but it is the best necessary condition that can be identified for compositionality of refinement.
+Like in the definition of simulation (Definition~\ref{def:HoleEqualSim}) we use guards to ensure that the transition can occur. 
+In general, one would not want to only consider non-blocking composition as it may reveal a bit restrictive, but it is the best necessary condition that can be identified for compositionality of simulation.
 It will be used to prove composition theorems in  Section~\ref{sec:prop}.
-Proving refinement relation in absence of non-blocking composition may also checked specifically for the composed automaton under study.
+Proving simulation relation in absence of non-blocking composition may also checked specifically for the composed automaton under study.
 %It is not sufficient to ensure the existence of equivalent transitions in general, but it will be sufficient in the context of refinement.
 
-\subsection{Automaton refinement}
-
-One major challenge in the extension of refinement to different sets of holes is to maintain a form of transitivity while being able to take into account the actions of some of the holes.
-A naive definition of refinement would ensure that only the holes that are identical in the two OA are taken into account in the simulation.
+\subsection{Automaton simulation}
+
+One major challenge in the extension of simulation to different sets of holes is to maintain a form of transitivity while being able to take into account the actions of some of the holes.
+A naive definition of simulation would ensure that only the holes that are identical in the two OA are taken into account in the simulation.
 Unfortunately considering all the common holes does not ensure transitivity of the simulation for the following reason.
-If $A_1$ simulates $A_2$ and $A_2$ simulates $A_3$, and one hole $j$ appears in $A_3$ and in $A_1$ but not in $A_2$ then we have no guarantee on the way $A_1$ and $A_3$ take the actions of this his hole into account, thus  a refinement between and $A_1$ and $A_3$ would require conditions involving actions of the hole $j$ which cannot be ensured.
+If $A_1$ simulates $A_2$ and $A_2$ simulates $A_3$, and one hole $j$ appears in $A_3$ and in $A_1$ but not in $A_2$ then we have no guarantee on the way $A_1$ and $A_3$ take the actions of this his hole into account, thus  a simulation between and $A_1$ and $A_3$ would require conditions involving actions of the hole $j$ which cannot be ensured.
 The way we solve this issue is to remember in the simulation relation which holes have been compared.
 This makes the relation parameterized by a subset of the set of holes that belong to the two automata that we want to take into account.
-This way, in the example above, we would have no guarantee on actions the hole $j$ by transitivity but can state a refinement relation with guarantees on the actions of the other holes.
-
-In the following definition we add a parameter $H$ which is the set of holes tracked by the refinement relation and adapt the definition by ignoring actions of the holes that are not in $H$.
+This way, in the example above, we would have no guarantee on actions the hole $j$ by transitivity but can state a simulation relation with guarantees on the actions of the other holes.
+
+In the following definition we add a parameter $H$ which is the set of holes tracked by the simulation relation and adapt the definition by ignoring actions of the holes that are not in $H$.
 \begin{definition}[Hole-tracking simulation]\label{Def:OA-Refinement}
-For two OA\\ \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a refinement of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a relation on configurations $R: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that:
-\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
+For two OA\\ \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a simulation of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a relation on configurations $\mathcal{R}: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that:
+\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash \mathcal{R}\mpar{s_{01}, s_{02}}\)
 \item[(2)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)
@@
 			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}   \nwedge\\
-			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+			 g_{2x} \wedge \mathcal{R}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
 		\end{array}}} 
@@
 \[
-\forall \mpar{s_1, s_2} \in S_1 \times S_2, V_1 \uplus V_2  \vdash R\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
+\forall \mpar{s_1, s_2} \!\in\!
+S_1 \!\times\!
+S_2, V_1 \uplus V_2  \vdash \mathcal{R}\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
 \]
 \end{definition}
-Note that every action of the holes outside \(H\) is unconstrained according to the refinement relation.
+Note that every action of the holes outside \(H\) is unconstrained according to the simulation relation.
 
@@
 \begin{property}[Relating simulations]\label{lem-sim-sim}
-Hole-equal simulation is a particular case of hole-tracking refinement when  $J_1=J_2=H$.
+Hole-equal simulation is a particular case of hole-tracking simulation when  $J_1=J_2=H$.
 \end{property}
@@
 
-\begin{property}[Tracked holes] By construction, if an automaton is the refinement of another one, it is also a refinement by tracking less holes.
+\begin{property}[Tracked holes] By construction, if an automaton is the simulation of another one, it is also a simulation by tracking less holes.
 \[\wrel{A_1}{A_2}{H} \land H'\subseteq H \implies \wrel{A_1}{A_2}{H'}\]
@@
 
-Now that we have a refinement relation that takes both variable parameters and process parameters into account, we would like to ensure that it has  properties one would expect for a refinement relation.
-
-\section{Properties of our Refinement Relations}\label{sec:prop}
-
-We now  state the properties of our refinement relations, proofs of the properties can be found in the appendices.
+Now that we have a simulation relation that takes both variable parameters and process parameters into account, we would like to ensure that it has  properties one would expect for a simulation relation.
+
+\section{Properties of our Simulation Relations}\label{sec:prop}
+
+We now  state the properties of our simulation, proofs of the properties can be found in the appendices.
 We express these properties in terms of hole-tracking simulation because, thanks to Property~\ref{lem-sim-sim}   all the properties  of hole-tracking simulation are also valid  for hole-equal simulation
-The first crucial property of  refinement  is that it is  a  preorder on the set of OA. This property enables stepwise refinement.
+The first crucial property of  simulation  is that it is  a  preorder on the set of OA. This property enables stepwise refinement.
 
@@
 The relation  \(\wrel{}{}{H}\) is reflexive,  \(\wrel{A}{A}{H}\).
-This is shown  by considering the relation $R$ such that $R\mpar{s_1, s_2} \triangleq s_1=s_2\land \displaystyle\bigwedge_\subbox{v \in vars(s_1)} {v=v}$   we can prove the conditions for Definition~\ref{Def:OA-Refinement}.
+This is shown  by considering the relation $\mathcal{R}$ such that $\mathcal{R}\mpar{s_1, s_2} \triangleq s_1=s_2\land \displaystyle\bigwedge_\subbox{v \in vars(s_1)} {v=v}$   we can prove the conditions for Definition~\ref{Def:OA-Refinement}.
 %
@@
 Appendix~\ref{sec:proof-transitivity} presents the proof of transitivity.
-It is done classically by identifying the relation between $A_1$ and $A_3$ that is a refinement.
+It is done classically by identifying the relation between $A_1$ and $A_3$ that is a simulation.
 What is less classical is the definition of this relation because it is a boolean formula.
-For each couple of states  $s_1$ and $s_3$ of $A_1$ and $A_3$ we build a  formula that defines the refinement relation.
+For each couple of states  $s_1$ and $s_3$ of $A_1$ and $A_3$ we build a  formula that defines the simulation.
 To do this, we take the disjunction of formulas relating $s_1$ and $s_3$, and passing by all states $s_2$ of $A_2$.
 More precisely, we define a relation of the following form:
-  \[R_{13}(s_1,s_3)=\bigvee_{s_2\in S_2}\mpar{R_{12}(s_1,s_2) \land R_{23}(s_2,s_3) } \]
-We then prove that this relation  is a refinement, according to Definition~\ref{Def:OA-Refinement}.
+  \[\mathcal{R}_{13}(s_1,s_3)=\bigvee_{s_2\in S_2}\mpar{\mathcal{R}_{12}(s_1,s_2) \land R_{23}(s_2,s_3) } \]
+We then prove that this relation  is a simulation, according to Definition~\ref{Def:OA-Refinement}.
 
@@
 
-The next  theorem states that if two automata are in refinement relation and the same automaton is placed in the same hole of the two automata, then the refinement is preserved.
+The next  theorem states that if two automata are in simulation relation and the same automaton is placed in the same hole of the two automata, then the simulation is preserved.
 This is the first step toward proving that
- refinement is compositional in the sense that it is sufficient to prove refinement for the composed automata separately to obtain a refinement relation.
-The second part,  proving that placing in the same context two OA in refinement, we obtain two OA in refinement is left for future works.
+ simulation is compositional in the sense that it is sufficient to prove simulation for the composed automata separately to obtain a simulation relation.
+%The second part,  proving that placing in the same context two OA in simulation, we obtain two OA in simulation is left for future works.
 %
@@
 
-The origins of the refinement are in the  approach of programming that aims to provide solid foundations for building correct programs \cite{Dijkstra76}.
+The origins of the simulation are in the  approach of programming that aims to provide solid foundations for building correct programs \cite{Dijkstra76}.
 There many work that contributed to the further development of the refinement calculus in various area (e.g.
@@
 As we shall see in this paper,
-our approach to design refinement  has some commonalities with that of the above mentioned \cite{deAlfaro:2021}: both are process-oriented approach even if they are not based on the same notion of simulation and they are based on optimistic approach to composition.
+our approach to design simulation  has some commonalities with that of the above mentioned \cite{deAlfaro:2021}: both are process-oriented approach even if they are not based on the same notion of simulation and they are based on optimistic approach to composition.
 For the composability, we use the notion of comparability of holes (similar to the notion of compatibility), which is explicitly encompassed in the definition of composition.
@@
 In this article we investigated the notion of refinement for a symbolic and open model: open automata. 
-OA are convenient for component-based software design.
-Indeed, OA allow the designer to model parallel systems that are parameterised both by the use of variables and by the possibility to compose automata.
-The formalism supports compositional specification through the refinement paradigm.
-The contribution of this paper, we introduce refinement  between open automata.
-The refinement relation  relies on a simulation relation between the specification and its implementation;  it  specifies that the refined process must follow the behaviour of the specification, not only at every compatible state but also along any trace.
-We finally showed that refinement is a preorder that is preserved when filling a hole.
-
-In the future we will focus on the other composition property that considers the preservation of refinement when automata are placed in the same context, namely filling the hole of the same automaton by an automaton and its refinement.
-This property should require some restriction on the composed processes.
- Finally, we will investigate under which condition, the composition operation produces a refinement in the sense that filling a hole produces a refined process.
+OA are convenient for compositional software verification.
+Indeed, OA  model parallel systems that are parameterised both by the use of variables and by the possibility to compose automata.
+The formalism supports compositional specification through the simulation paradigm.
+In this paper, we introduce a refinement relation  between open automata.
+It relies on a simulation relation between the two automata;  it  specifies that the refined process must follow the behaviour of the simulated one.
+We finally showed that simulation is a preorder that is preserved by composition, both when filling a hole and when placing auomata in comparable contexts.
+
+In the future, we will investigate under which condition, the composition operation produces a refinement in the sense that filling a hole produces a refined process.
 
@@
 \proof 
-If $\wrel{A_1}{A_2}{H}$ then there is $R_{12}$ a relation between states
-of $A_1$ and of $A_2$;  If $\wrel{A_2}{A_3}{H'}$ then there is $R_{23}$ a relation between states of $A_2$ and of $A_3$. We build a relation between
- states of $A_1$ and of $A_3$ as follows:  for each pair of states $s_1$, $s_3$, for each state $s_2$ such that $R_{12}$ relates $s_1$ and $s_2$, and $R_{23}$ relates $s_2$ and $s_3$.
-Let $R_{13}$ be the relation:\\
-  \[R_{13}(s_1,s_3)=\bigvee_{s_2\in S_2}\mpar{R_{12}(s_1,s_2) \land R_{23}(s_2,s_3) } \]
-
-We will show that $\wrel{A_1}{A_3}{H\cap H'}$ by exhibiting  $R_{13}$ as a hole-tracking simulation of $A_1$ by  $A_3$.
-
-We have to prove that the relation $R_{13}$ satisfies the three conditions of the definition of a refinement of OA.
+If $\wrel{A_1}{A_2}{H}$ then there is $\mathcal{R}_{12}$ a relation between states
+of $A_1$ and of $A_2$;  If $\wrel{A_2}{A_3}{H'}$ then there is $ˇ_{23}$ a relation between states of $A_2$ and of $A_3$. We build a relation between
+ states of $A_1$ and of $A_3$ as follows:  for each pair of states $s_1$, $s_3$, for each state $s_2$ such that $\mathcal{R}_{12}$ relates $s_1$ and $s_2$, and $\mathcal{R}_{23}$ relates $s_2$ and $s_3$.
+Let $\mathcal{R}_{13}$ be the relation:\\
+  \[\mathcal{R}_{13}(s_1,s_3)=\bigvee_{s_2\in S_2}\mpar{\mathcal{R}_{12}(s_1,s_2) \land \mathcal{R}_{23}(s_2,s_3) } \]
+
+We will show that $\wrel{A_1}{A_3}{H\cap H'}$ by exhibiting  $\mathcal{R}_{13}$ as a hole-tracking simulation of $A_1$ by  $A_3$.
+
+We have to prove that the relation $\mathcal{R}_{13}$ satisfies the three conditions of the definition of a refinement of OA.
 \begin{enumerate}
-\item Firstly, we have to $R_{13}$ satisfies initial configurations:
-\[\sigma_{01} \uplus \sigma_{03} \vdash R_{13} \mpar{s_{01}, s_{03}}\]
+\item Firstly, we have to $\mathcal{R}_{13}$ satisfies initial configurations:
+\[\sigma_{01} \uplus \sigma_{03} \vdash \mathcal{R}_{13} \mpar{s_{01}, s_{03}}\]
 By knowing that substitutions only have an effect on the variables of the OA they belong to, they also produce terms containing only variables of the OA they belong to. We have:
 \begin{align*}
-\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar
-{\sigma_{02} \uplus \sigma_{03} \vdash R_{23}\mpar{s_{02}, s_{03}}}&\implies\\
-R_{12}\mpar{s_{01},s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02}} \wedge R_{23}\mpar{s_{02}, s_{03}}\psubst{\sigma_{02} \uplus \sigma_{03}}&\implies\\
-R_{12}\mpar{s_{01},s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} \wedge R_{23}\mpar{s_{02}, s_{03}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}}&\implies\\ 
-\underbrace{R_{12}\mpar{s_{01},s_{02}}\wedge R_{23}\mpar{s_{02}, s_{03}}}_{\implies R_{13} \mpar{s_{01}, s_{03}}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} %&\implies\\
+\mpar{\sigma_{01} \uplus \sigma_{02} \vdash \mathcal{R}_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar
+{\sigma_{02} \uplus \sigma_{03} \vdash \mathcal{R}_{23}\mpar{s_{02}, s_{03}}}&\implies\\
+\mathcal{R}_{12}\mpar{s_{01},s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02}} \wedge \mathcal{R}_{23}\mpar{s_{02}, s_{03}}\psubst{\sigma_{02} \uplus \sigma_{03}}&\implies\\
+\mathcal{R}_{12}\mpar{s_{01},s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} \wedge \mathcal{R}_{23}\mpar{s_{02}, s_{03}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}}&\implies\\
+\underbrace{\mathcal{R}_{12}\mpar{s_{01},s_{02}}\wedge \mathcal{R}_{23}\mpar{s_{02}, s_{03}}}_{\implies \mathcal{R}_{13} \mpar{s_{01}, s_{03}}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} %&\implies\\
  \end{align*}
@@
 \item Lastly, we have to prove the satisfaction of the deadlock reduction condition. 
- To build $R_{13}$ we need to rely on the disjunction of all possible paths to relate $s_1$ and $s_3$, which leads to \[{\displaystyle R_{13}(s_1,s_3)=\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1,s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}}\]
-
-Consider any $\mpar{s_{1}, s_{3}} \in R_{13}$  there is a set of states $(s_{2p})^{p\in P}$ of $A_2$ relating  $s_{1}$ and $s_{3}$.
+ To build $\mathcal{R}_{13}$ we need to rely on the disjunction of all possible paths to relate $s_1$ and $s_3$, which leads to \[{\displaystyle \mathcal{R}_{13}(s_1,s_3)=\bigvee_{{p\in P}}\mpar{\mathcal{R}_{12}\mpar{s_1,s_{2p}} \wedge \mathcal{R}_{23}\mpar{s_{2p},s_3}}}\]
+
+Consider any $\mpar{s_{1}, s_{3}} \in \mathcal{R}_{13}$  there is a set of states $(s_{2p})^{p\in P}$ of $A_2$ relating  $s_{1}$ and $s_{3}$.
 
@@
 %\forall \mpar{s_1, s_{2p}} \in S_1 \times S_2, 
-V_1 \uplus V_2  \vdash R_{12}\mpar{s_1, s_{2p}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}  \lor¢ \lnot( \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}}  )
+V_1 \uplus V_2  \vdash \mathcal{R}_{12}\mpar{s_1, s_{2p}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}  \lor¢ \lnot( \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}}  )
 \end{multline*}
@@
 \begin{multline*}
- V_2 \uplus V_3  \vdash R_{23}\mpar{s_{2p},s_3} \implies  \bigvee_\subbox{t_1 \in \fOT{s_{2p}}} \fguard{t_{2p}}  \lor¢ \lnot( \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} )
+ V_2 \uplus V_3  \vdash \mathcal{R}_{23}\mpar{s_{2p},s_3} \implies  \bigvee_\subbox{t_1 \in \fOT{s_{2p}}} \fguard{t_{2p}}  \lor¢ \lnot( \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} )
 \end{multline*}
@@
 \begin{multline*}
- V_1 \uplus V_2 \uplus V_3  \vdash  R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3} \implies   \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} 
+ V_1 \uplus V_2 \uplus V_3  \vdash  \mathcal{R}_{12}\mpar{s_1, s_{2p}} \wedge \mathcal{R}_{23}\mpar{s_{2p},s_3} \implies \\
+  \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} 
  \lor¢ \lnot( \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} )
@@
 \begin{multline*}
- V_1 \uplus V_2 \uplus V_3  \vdash \underbrace{\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}}_{R_{13}(s_1,s_3)} \implies  ( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )
+ V_1 \uplus V_2 \uplus V_3  \vdash \underbrace{\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}}_{R_{13}(s_1,s_3)} \implies \\ ( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )
  \lor¢ \lnot( \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} )
@@
 \begin{multline*}
- V_1 \uplus  V_3  \vdash R_{13}(s_1,s_3) \implies  ( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )
+ V_1 \uplus  V_3  \vdash \mathcal{R}_{13}(s_1,s_3) \implies  ( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )
  \lor¢ \lnot( \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} )
@@
 
-Let $R$ be the refinement relation relating states of $A_1$ and $A_2$. 
+Let $\mathcal{R}$ be the refinement relation relating states of $A_1$ and $A_2$. 
 Let us denote with $t^1$ and $t^2$  the elements of $A_1$ and $A_2$ respectively.
 Consider any two states $s_{13} = \mpar{s_1,s^1_3}$ and $s_{23} = \mpar{s_2,s^2_3}$ ($s^1_3$ and $s^2_3$  are the same with renaming).
-We define a relation $R'$ relating states of $s_{13}$ and $s_{23}$ as follows:
-\[ R' \mpar{s_{13}, s_{23}} = R\mpar{s_{1}, s_{2}} \land \reach{A_{13}}(s_{13})  %\wedge \reach{A_{13}}\mpar{s_{13}}
+We define a relation $\mathcal{R}'$ relating states of $s_{13}$ and $s_{23}$ as follows:
+\[ \mathcal{R}' \mpar{s_{13}, s_{23}} = \mathcal{R}\mpar{s_{1}, s_{2}} \land \reach{A_{13}}(s_{13})  %\wedge \reach{A_{13}}\mpar{s_{13}}
  \wedge \bigwedge_\subbox{v_3\in V_3}
@@
 
-We want to prove that $\mpar{R', H\uplus J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$. In the following we denote $H'=H\cup J_3 \setminus\{k\}$.
+We want to prove that $\mpar{\mathcal{R}', H\uplus J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$. In the following we denote $H'=H\cup J_3 \setminus\{k\}$.
 \begin{enumerate}
 \item First, we have to prove the relation for initial states:
-\[\sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}\]
+\[\sigma_{013} \uplus \sigma_{023} \vdash \mathcal{R}'\mpar{s_{013}, s_{023}}\]
 with $\sigma_{013} = \sigma_{01} \uplus \sigma_{03}^1$, $\sigma_{023} = \sigma_{02} \uplus \sigma_{03}^2$, $s_{013}=(s_{01},s_{03}^1)$, and $s_{023}=(s_{02},s_{02}^2)$.\\
-By using the fact that $R$ relates initial configurations of  $A_1$ and $A_2$, we have:
+By using the fact that $\mathcal{R}$ relates initial configurations of  $A_1$ and $A_2$, we have:
 $\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}}$.  

### 2023-06-19 2021-Refinement/paper/refinementarticleV2.tex
notatinos again

@@
 By using the fact that $\mathcal{R}$ relates initial configurations of  $A_1$ and $A_2$, we have:
-$\mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}}$.  
+$\mpar{\sigma_{01} \uplus \sigma_{02} \vdash \mathcal{R}\mpar{s_{01}, s_{02}}}$.  
 %and based on the  fact that initial states are reachable $\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ we have 
@@
 \begin{align*}
-& \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} 
+& \mpar{\sigma_{01} \uplus \sigma_{02} \vdash \mathcal{R}\mpar{s_{01}, s_{02}}} 
 %\wedge \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}
 \\
-\implies & R\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}}  \land \mpar{\,\,\bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }\\
-\implies & \mpar{R\mpar{s_{01}, s_{02}} \wedge  \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma^1_{03}\uplus \sigma^2_{03}\uplus \sigma_{013} }\\
-\implies & \sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}
+\implies & \mathcal{R}\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}}  \land \mpar{\,\,\bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }\\
+\implies & \mpar{\mathcal{R}\mpar{s_{01}, s_{02}} \wedge  \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma^1_{03}\uplus \sigma^2_{03}\uplus \sigma_{013} }\\
+\implies & \sigma_{013} \uplus \sigma_{023} \vdash \mathcal{R}'\mpar{s_{013}, s_{023}}
 \end{align*}
@@
 		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\
-		& R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+		& \mathcal{R}'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
 			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \wedge\\[12pt]
-			 g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
+			 g_{23x} \wedge \mathcal{R}'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
 		\end{array}} 
@@
 %\everymath{\displaystyle}
-V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\ \mpar{R\mpar{s_1, s_{2}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\ \mpar{\mathcal{R}\mpar{s_1, s_{2}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
 \begin{array}{l}
 			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \nwedge\\
-			 g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+			 g_{2x} \wedge \mathcal{R}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
 		\end{array}}}  \qquad \quad (*)
@@
 V_{13} \uplus V_{23}  \uplus \fvars{t_{13}} \vdash\\
-R\mpar{s_1, s_{2}} \wedge \mpar{g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}}\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3 %\wedge s^1_3=s^2_3
+\mathcal{R}\mpar{s_1, s_{2}} \wedge \mpar{g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}}\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3 %\wedge s^1_3=s^2_3
 \implies  \hspace{12em}\\
@@
 			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in (J'_{23x} \cap H')} \beta_{13j}\! =\! \beta_{23xj}\nwedge\\
-			  g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+			  g_{2x} \wedge \mathcal{R}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
 		\end{array}}  \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk} 
@@
 V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
-R\mpar{s_1, s_{2}} \wedge g_{13}  \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3
+\mathcal{R}\mpar{s_1, s_{2}} \wedge g_{13}  \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3
 \implies  \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
@@
 			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge\\
-			g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+			g_{23x} \wedge \mathcal{R}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
 		\end{array}}   
@@
 V_{13} \uplus V_{23} \uplus \fvars{t_1}  \cap \fvars{t_{13}} \vdash\\
-R\mpar{s_1, s_{2}} \wedge g_{13}  {\wedge \reach{A_{13}}\mpar{s_{13}}}
+\mathcal{R}\mpar{s_1, s_{2}} \wedge g_{13}  {\wedge \reach{A_{13}}\mpar{s_{13}}}
 \wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
@@
 \begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge 	g_{23x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\\
+			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge 	g_{23x} \wedge \mathcal{R}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\\
 		  \wedge {\reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
@@
 V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
-R\mpar{s_1, s_{2}} \wedge g_{13} \land {\reach{A_{13}}\mpar{s_{13}} \land} \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3 \wedge s^1_3 = s^2_3
+\mathcal{R}\mpar{s_1, s_{2}} \wedge g_{13} \land {\reach{A_{13}}\mpar{s_{13}} \land} \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3 \wedge s^1_3 = s^2_3
 \implies \hspace{7em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
@@
 			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\land  {\reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}}		\nwedge\\
-			  R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge
+			  \mathcal{R}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge
  \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3) \wedge s^{1\prime}_3 = s^{2\prime}_3
@@
 	\begin{multline*}
-  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ R^{\prime}\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ \mathcal{R}^{\prime}\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
 			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge\\[12pt]
-			 g_{23x} \wedge R^{\prime}\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
+			 g_{23x} \wedge \mathcal{R}^{\prime}\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
 		\end{array}} 
@@
 \begin{multline*}
-V_{13} \uplus V_{23}  \vdash  R\mpar{s_{13}, s_{23}} \nwedge  \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}) \implies   \neg (\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}) 
+V_{13} \uplus V_{23}  \vdash  \mathcal{R}\mpar{s_{13}, s_{23}} \nwedge  \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}) \implies   \neg (\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
 \end{multline*}
@@
 \begin{multline*}
-V_1 \uplus V_2 \vdash R\mpar{s_1, s_2} \nwedge \neg (\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}) \implies   \neg(\bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2})
+V_1 \uplus V_2 \vdash \mathcal{R}\mpar{s_1, s_2} \nwedge \neg (\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}) \implies   \neg(\bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2})
 \end{multline*}
@@
 \begin{multline*}
-V_{13} \uplus V_{23}  \vdash  \underbrace{R\mpar{s_1, s_2} \wedge \reach{A_{13}}(s_{13}) \land \mpar{\,\,\bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3 \wedge s^1_3=s^2_3}}_{R^{\prime}(s_{13},s_{23})} \wedge \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})   \\ \implies \left(\neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}) \lor \neg{\reach{A_{13}}(s_{13}) }\right) \land \reach{A_{13}}(s_{13})\\
+V_{13} \uplus V_{23}  \vdash  \underbrace{\mathcal{R}\mpar{s_1, s_2} \wedge \reach{A_{13}}(s_{13}) \land \mpar{\,\,\bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3 \wedge s^1_3=s^2_3}}_{\mathcal{R}^{\prime}(s_{13},s_{23})} \wedge \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})   \\ \implies \left(\neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}) \lor \neg{\reach{A_{13}}(s_{13}) }\right) \land \reach{A_{13}}(s_{13})\\
 \implies \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
@@
 Consider any two states $s_{12} = \mpar{s^1_1,s_2}$ and $s_{13} = \mpar{s^2_1,s_3}$ ($s^1_1$ and $s^2_1$  are the same with renaming).
-We define a relation $R'$ relating states of $s_{12}$ and $s_{13}$ as follows:
-\[ R' \mpar{s_{12}, s_{13}} = R\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1}
+We define a relation $\mathcal{R}'$ relating states of $s_{12}$ and $s_{13}$ as follows:
+\[\mathcal{R}' \mpar{s_{12}, s_{13}} = \mathcal{R}\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1}
  v^1_1=v^2_1\wedge s^1_1 = s^2_1\]
 Let us denote $H'=H\cup J_1 \setminus\{k\}$.
-We want to prove that $\mpar{R', H'}$  is a hole-tracking simulation of $A_{12}$ and $A_{13}$. As for the previous proof we deal with cases:
+We want to prove that $\mpar{\mathcal{R}', H'}$  is a hole-tracking simulation of $A_{12}$ and $A_{13}$. As for the previous proof we deal with cases:
 \begin{enumerate}
@@
 \begin{multline*}	
-V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ R'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
+V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ \mathcal{R}'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
 			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \wedge\\[12pt]
-			 g_{13x} \wedge R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
+			 g_{13x} \wedge \mathcal{R}'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
 		\end{array}} 
@@
 %\everymath{\displaystyle}
-V_2 \uplus V_3 \uplus \fvars{t_2} \vdash\\ R\mpar{s_2, s_3} \wedge g_2 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+V_2 \uplus V_3 \uplus \fvars{t_2} \vdash\\ \mathcal{R}\mpar{s_2, s_3} \wedge g_2 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
 \begin{array}{l}
 			\alpha_2 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj} \nwedge\\
-			 g_{3x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
+			 g_{3x} \wedge \mathcal{R}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
 		\end{array}}  \qquad \quad (*)
@@
 & =((J'_{3x}\cap H)\uplus J^{2 \prime}_{1})\setminus \mbrc{k}\text{ since } J^{2 \prime}_{1}\subseteq J_1\\
-& =((J'_2\cap H)\uplus J^{1 \prime}_{1})\setminus \mbrc{k} \text{ since } J^{1 \prime}_{1}=J^{2 \prime}_{1} \text{ and } J'_2 \cap H = J'_{3x} \cap H\\
+& =((J'_2\cap H)\uplus J^{1 \prime}_{1})\setminus \mbrc{k}\\
+& \qquad\qquad\qquad \text{ since } J^{1 \prime}_{1}=J^{2 \prime}_{1} \text{ and } J'_2 \cap H = J'_{3x} \cap H\\
 &= ((J'_2 \cap H) \uplus (J^{1 \prime}_{1} \cap J_1)) \setminus \mbrc{k}\text{ since } J^{1 \prime}_{1}\subseteq J_1\\ 
@@
 V_{13} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash\\
-R\mpar{s_2, s_{3}} \wedge \mpar{g_2 \wedge g^1_1 \wedge \alpha^1_1=\beta_{2k}}\wedge \bigwedge_\subbox{v_1\in V_1}  v^1_1=v^2_1 %\wedge s^1_1=s^2_1
+\mathcal{R}\mpar{s_2, s_{3}} \wedge \mpar{g_2 \wedge g^1_1 \wedge \alpha^1_1=\beta_{2k}}\wedge \bigwedge_\subbox{v_1\in V_1}  v^1_1=v^2_1 %\wedge s^1_1=s^2_1
 \implies  \hspace{12em}\\
@@
 			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in (J'_{13x} \cap H')} \beta_{12j}\! =\! \beta_{13xj}\nwedge\\
-			  g_{3x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
+			  g_{3x} \wedge \mathcal{R}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
 		\end{array}}  \wedge g^2_1 \wedge \alpha^2_1=\beta_{3xk} 
@@
 V_{12} \uplus V_{13} \uplus \fvars{t_{12}}  \vdash\\
-R\mpar{s_2, s_{3}} \wedge g_{12}  \land \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1
+\mathcal{R}\mpar{s_2, s_{3}} \wedge g_{12}  \land \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1
 \implies  \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
@@
 			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge\\
-			g_{13x} \wedge R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
+			g_{13x} \wedge \mathcal{R}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
 		\end{array}}   
@@
 V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash\\
-R\mpar{s_2, s_{3}} \wedge g_{12} \land \reach{A_{12}}\mpar{s_{12}} \land \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1  \wedge s^1_1 = s^2_1 
+\mathcal{R}\mpar{s_2, s_{3}} \wedge g_{12} \land \reach{A_{12}}\mpar{s_{12}} \land \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1  \wedge s^1_1 = s^2_1 
 \implies \hspace{12em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
@@
 			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge g_{13x} \wedge \\
-			 R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}} \land \reach{A_{12}}\mpar{s_{12}'}\psubst{\psi_{12}} \\
+			 \mathcal{R}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}} \land \reach{A_{12}}\mpar{s_{12}'}\psubst{\psi_{12}} \\
 \wedge \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{13x}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1
@@
 V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash
-R'\mpar{s_{12}, s_{13}} \wedge g_{12} 
+\mathcal{R}'\mpar{s_{12}, s_{13}} \wedge g_{12} 
 \implies \hspace{10em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
@@
 			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge g_{13x} \wedge 
-			 R'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
+			 \mathcal{R}'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
 		\end{array}}   
@@
 Moreover, we have by definition 
-\[R' \mpar{s_{12}, s_{13}} =  R\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge s^1_1 = s^2_1 \]
+\[\mathcal{R}' \mpar{s_{12}, s_{13}} =  \mathcal{R}\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge s^1_1 = s^2_1 \]
 Thus, because transitions $t^1_1$ and  $t^2_1$ are the same:
-\[R' \mpar{s_{12}, s_{13}} \implies
-\underbrace{R\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge {s^1_1}^\prime = {s^2_1}^\prime}_{R' \mpar{s'_{12}, s'_{13}}}
+\[\mathcal{R}' \mpar{s_{12}, s_{13}} \implies
+\underbrace{\mathcal{R}\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge {s^1_1}^\prime = {s^2_1}^\prime}_{\mathcal{R}' \mpar{s'_{12}, s'_{13}}}
 \]
@@
 V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash
-R'\mpar{s_{12}, s_{13}} \wedge g_{12} 
+\mathcal{R}'\mpar{s_{12}, s_{13}} \wedge g_{12} 
 \implies \hspace{10em}\\ %\operatorname*{\bigsymb{\bigvee}}_{x \in X}
@@
 			\alpha_{12} = \alpha_{13} \wedge \bigwedge_\subbox{j \in J'_{13} \cap H'} \beta_{12j} = \beta_{13j} \nwedge g_{13} \wedge 
-			 R'\mpar{s'_{12}, s'_{13}}\psubst{\psi_{12} \uplus \psi_{13}}
+			 \mathcal{R}'\mpar{s'_{12}, s'_{13}}\psubst{\psi_{12} \uplus \psi_{13}}
 %		\end{array}
@@
 \begin{multline*}
-V_{12} \uplus V_{13}  \vdash  R'\mpar{s_{12}, s_{13}} \nwedge  \neg(\bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}) \implies   \neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})
+V_{12} \uplus V_{13}  \vdash  \mathcal{R}'\mpar{s_{12}, s_{13}} \nwedge  \neg(\bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}) \implies   \neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})
 \end{multline*}
@@
 \begin{multline*}
-V_2 \uplus V_3  \vdash R\mpar{s_2, s_3} \nwedge \neg (\bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}) \implies   \neg(\bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3})
+V_2 \uplus V_3  \vdash\mathcal{R}\mpar{s_2, s_3} \nwedge \neg (\bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}) \implies   \neg(\bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3})
 \end{multline*}
@@
 \neg{ \bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}}
-\implies 
+\implies \\
 \left(\neg{\reach{A_{12}(s_{12})} }\lor \neg{\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
@@
 
-Thus we have, as $R$ contains the reachability of state $s_{12}$:\TODO{faire une jolie equation}
-\begin{multline*}
-V_{12} \uplus V_{13}  \vdash  R'\mpar{s_{12}, s_{13}} \nwedge  \neg(\bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}) \\
+Thus we have, as $\mathcal{R}$ contains the reachability of state $s_{12}$:\TODO{faire une jolie equation}
+\begin{multline*}
+V_{12} \uplus V_{13}  \vdash  \mathcal{R}'\mpar{s_{12}, s_{13}} \nwedge  \neg(\bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}) \\
 \implies \reach{A_{12}(s_{12})} \land \left(\neg{\reach{A_{12}(s_{12})} }\lor

### 2023-06-19 2021-Refinement/paper/refinementarticleV2.tex
End of big read

@@
 %
-\title{Refinements for open automata}
+\title{Refinements for Open Automata}
 
@@
 
-\begin{definition}[Composition of open automata] \label{Def:CompOA}
+\begin{definition}[Composition of OA] \label{Def:CompOA}
 % TODO: this definition is a bit strange, why is Ac in the hole of Ap but the hole is in Ac and the notation is reversed?
-Let  \(A_c = \OAg[c]\) be a context OA and $k$ one of its holes, \(k \in J_c\). Let \(A_p = \OAg[p]\) be an OA,  the composition $A_c\subst{A_p}{k}$ is defined as follows:
+Let  \(A_c = \OAg[c]\) be an OA and $k$ one of its holes, \(k \in J_c\).
+Let \(A_p = \OAg[p]\) be another OA,  the composition $A_c\subst{A_p}{k}$ that fills the hole $k$ of the context OA \(A_c\) with the parameter OA \(A_p\) is defined as follows:
 \[A_c\subst{A_p}{k} ::=  \OA{S_c \times S_p}{\mpar{s_{0c}, s_{0p}}}{V_c \uplus V_p}{\sigma_{0c} \uplus \sigma_{0p}}{J_p \uplus J_c \setminus \mbrc{k}}{T} \] \text{with }
@@
 
-\subsection{Relations between open automata}
+\subsection{Relations between Open Automata}
 Establishing semantic equivalences and simulation relations between different OA requires  to compare their states.
@@
 
-\subsection{A bisimulation for open automata}
+\subsection{A Bisimulation for Open Automata}
 
@@
 
-\section{Simulation Relations for automata with the same holes}\label{sec:refinement}
+\section{Simulation  for Automata with the Same Holes}\label{sec:refinement}
 
@@
 This section  extends the preceding relation to automata where the set of holes is not the same. 
-Indeed, when composing the set of  holes changes, and for example we want to state whether the automaton after composition is a simulation of the original automaton or not.
-
-\subsection{Deadlock Reduction, Reachability, and Composition}
+This is particularly useful  to state whether the automaton after composition is a simulation of the original automaton or not.
+Indeed, when composing the set of  holes changes.
+Being able to compare automata with only some of their holes in common seems useful in general.
+
+\medskip
+One major challenge in the extension of simulation to different sets of holes is to maintain a form of transitivity while being able to take into account the actions of some of the holes.
+A naive definition of simulation would ensure that only the holes that are identical in the two OA are taken into account in the simulation.
+Unfortunately considering all the common holes does not ensure transitivity of the simulation for the following reason.
+If $A_1$ simulates $A_2$ and $A_2$ simulates $A_3$, and one hole $j$ appears in $A_3$ and in $A_1$ but not in $A_2$ then we have no guarantee on the way $A_1$ and $A_3$ take the actions of this his hole into account, thus  a simulation between and $A_1$ and $A_3$ would require conditions involving actions of the hole $j$ which cannot be ensured.
+The way we solve this issue is to remember in the simulation relation which holes have been compared.
+This makes the relation parameterized by a subset of the set of holes that belong to the two automata that we want to take into account.
+This way, in the example above, we would have no guarantee on actions the hole $j$ by transitivity but can state a simulation relation with guarantees on the actions of the other holes.
+
+In the following definition we add a parameter $H$ which is the set of holes tracked by the simulation relation and adapt the definition by ignoring actions of the holes that are not in $H$.
+\begin{definition}[Hole-tracking simulation]\label{Def:OA-Refinement}
+For two OA\\ \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a simulation of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a relation on configurations $\mathcal{R}: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that:
+\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash \mathcal{R}\mpar{s_{01}, s_{02}}\)
+\item[(2)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)
+\begin{multline*}
+	\everymath{\displaystyle}\begin{array}{l}
+		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\[12pt]
+		\quad \mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H} \nwedge\\[1pt]
+		 V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\\hspace{5em} \mpar{R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}   \nwedge\\
+			 g_{2x} \wedge \mathcal{R}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
+		\end{array}}} 
+	\end{array} 
+\end{multline*}
+\item[(3)] Deadlock reduction:
+\[
+\forall \mpar{s_1, s_2} \!\in\!
+S_1 \!\times\!
+S_2, V_1 \uplus V_2  \vdash \mathcal{R}\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
+\]
+\end{definition}
+Note that every action of the holes outside \(H\) is unconstrained according to the simulation relation.
+
+%\begin{example} It is easy to see the  open automaton of Fig.~\ref{Fig:RefineOA} is a refinement the open automaton of Fig.~\ref{Fig:SpecOA} according to this definition.
+%\end{example}
+
+\begin{property}[Relating simulations]\label{lem-sim-sim}
+Hole-equal simulation is a particular case of hole-tracking simulation when  $J_1=J_2=H$.
+\end{property}
+\begin{example} Consider the automata of examples \ref{Example:fifo-system} and \ref{example:fifo-system-one}.
+As we saw above, \texttt{prod-cons} $\leq$ \texttt{simprod-cons}, therefore \texttt{prod-cons} $\leq_{\{\texttt{P,Q}\}}$ \texttt{simprod-cons}.
+\end{example}
+%\TODO{potential ex 4: check if the example with a hole filled is a simulation of the example with holes? }
+
+%
+%\TODO{
+%A string $t \in \mathcal{A}^*$ is a trace of an automaton if there is some state $s$ such that $s_0 \xrightarrowdbl{t}  s$. We denote the set of traces of an automaton $A$ by $\mathcal{T}_A$. \\
+%Notion of Extension refinement. May be we need to introduce the notion of  refusal of
+%a trace $t \in \mathcal{T}_A$ is a set of actions such that all actions in the set can be refused after the automaton $A$
+%has executed the trace $t$.
+\[X \in \bot_{A}(t) \Leftrightarrow \{\exists s.
+s_0  \xrightarrowdbl{t} s \wedge \forall a \in X.
+s \not{\xrightarrow{a}}    \}\] and replace deadlock reducing, under (3) by
+%\[\forall t \in \mathcal{T}_{A_1} \cap  \mathcal{T}_{A_2},\, \bot_{A_2}(t) \subseteq  \bot_{A_1}(t)  \] } 
+%
+%\TODO{thm: backward compatibility + simulation is equivalent to extension refinement in case there is no hole and no guard, i.e. in case the definitions of automata coincide}
+
+\begin{property}[Tracked holes] By construction, if an automaton is the simulation of another one, it is also a simulation by tracking less holes.
+\[\wrel{A_1}{A_2}{H} \land H'\subseteq H \implies \wrel{A_1}{A_2}{H'}\]
+\end{property}
+
+Now that we have a simulation relation that takes both variable parameters and process parameters into account, we would like to ensure that it has  properties one would expect for a simulation relation.
+
+\section{Properties of our Simulation Relations}\label{sec:prop}
+
+Before reasoning on the properties of simulation. we need to introduce one additional notion that characterizes when the composition of two automata does not introduce new blocked transitions.
+
+\subsection{Non-blocking Composition}
 
@@
 \begin{definition}[Non-blocking composition] \label{Def:Non-block}
-Let \(A_1 \defobject \OAg[1]\) and \( A_2 \defobject \OAg[2]\) be two OA.
-Let $A= \OAg$ be the OA resulting from the composition \(A = A_1\subst{A_2}{k}\). 
+Consider two OA:\\ \(A_1 \defobject \OAg[1]\) and \( A_2 \defobject \OAg[2]\).
+Let $A$ be the OA resulting from the composition \(A = A_1\subst{A_2}{k}= \OAg\). 
 The composition \(A_1\subst{A_2}{k}\) is non-blocking if   \(A \) has a reachability predicate such that, for each reachable configuration, if there is a possible transition in \(A_1\) then there is a possible transition in \(A\):
-\begin{multline*}
- \forall s = \mpar{s_1, s_2} \in S, V \uplus \biguplus_\subbox{t \in \fOT{s_1}} \fvars{t} \vdash  \left(\reach{A}\mpar{s} \wedge \bigvee_\subbox{t \in \fOT{s_1}} \fguard{t} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \right)
-\end{multline*}
+%\begin{multline*}
+\[ \forall s = \mpar{s_1, s_2} \in S, V \uplus \biguplus_\subbox{t \in \fOT{s_1}} \fvars{t} \vdash  \left(\reach{A}\mpar{s} \wedge \bigvee_\subbox{t \in \fOT{s_1}} \fguard{t} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \right)
+\]
+%\end{multline*}
 \end{definition}
@@
 In general, one would not want to only consider non-blocking composition as it may reveal a bit restrictive, but it is the best necessary condition that can be identified for compositionality of simulation.
-It will be used to prove composition theorems in  Section~\ref{sec:prop}.
-Proving simulation relation in absence of non-blocking composition may also checked specifically for the composed automaton under study.
+It will be used to prove composition theorems below.
+In absence of non-blocking composition, simulation may also be checked specifically for a given composed automaton.
 %It is not sufficient to ensure the existence of equivalent transitions in general, but it will be sufficient in the context of refinement.
 
-\subsection{Automaton simulation}
-
-One major challenge in the extension of simulation to different sets of holes is to maintain a form of transitivity while being able to take into account the actions of some of the holes.
-A naive definition of simulation would ensure that only the holes that are identical in the two OA are taken into account in the simulation.
-Unfortunately considering all the common holes does not ensure transitivity of the simulation for the following reason.
-If $A_1$ simulates $A_2$ and $A_2$ simulates $A_3$, and one hole $j$ appears in $A_3$ and in $A_1$ but not in $A_2$ then we have no guarantee on the way $A_1$ and $A_3$ take the actions of this his hole into account, thus  a simulation between and $A_1$ and $A_3$ would require conditions involving actions of the hole $j$ which cannot be ensured.
-The way we solve this issue is to remember in the simulation relation which holes have been compared.
-This makes the relation parameterized by a subset of the set of holes that belong to the two automata that we want to take into account.
-This way, in the example above, we would have no guarantee on actions the hole $j$ by transitivity but can state a simulation relation with guarantees on the actions of the other holes.
-
-In the following definition we add a parameter $H$ which is the set of holes tracked by the simulation relation and adapt the definition by ignoring actions of the holes that are not in $H$.
-\begin{definition}[Hole-tracking simulation]\label{Def:OA-Refinement}
-For two OA\\ \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a simulation of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a relation on configurations $\mathcal{R}: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that:
-\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash \mathcal{R}\mpar{s_{01}, s_{02}}\)
-\item[(2)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)
-\begin{multline*}
-	\everymath{\displaystyle}\begin{array}{l}
-		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\[12pt]
-		\quad \mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H} \nwedge\\[1pt]
-		 V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\\hspace{5em} \mpar{R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}   \nwedge\\
-			 g_{2x} \wedge \mathcal{R}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}}} 
-	\end{array} 
-\end{multline*}
-\item[(3)] Deadlock reduction:
-\[
-\forall \mpar{s_1, s_2} \!\in\!
-S_1 \!\times\!
-S_2, V_1 \uplus V_2  \vdash \mathcal{R}\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
-\]
-\end{definition}
-Note that every action of the holes outside \(H\) is unconstrained according to the simulation relation.
-
-%\begin{example} It is easy to see the  open automaton of Fig.~\ref{Fig:RefineOA} is a refinement the open automaton of Fig.~\ref{Fig:SpecOA} according to this definition.
-%\end{example}
-
-\begin{property}[Relating simulations]\label{lem-sim-sim}
-Hole-equal simulation is a particular case of hole-tracking simulation when  $J_1=J_2=H$.
-\end{property}
-\begin{example} Consider the automata of examples \ref{Example:fifo-system} and \ref{example:fifo-system-one}.
-As we saw above, \texttt{prod-cons} $\leq$ \texttt{simprod-cons}, therefore \texttt{prod-cons} $\leq_{\{\texttt{P,Q}\}}$ \texttt{simprod-cons}.
-\end{example}
-%\TODO{potential ex 4: check if the example with a hole filled is a simulation of the example with holes? }
-
-%
-%\TODO{
-%A string $t \in \mathcal{A}^*$ is a trace of an automaton if there is some state $s$ such that $s_0 \xrightarrowdbl{t}  s$. We denote the set of traces of an automaton $A$ by $\mathcal{T}_A$. \\
-%Notion of Extension refinement. May be we need to introduce the notion of  refusal of
-%a trace $t \in \mathcal{T}_A$ is a set of actions such that all actions in the set can be refused after the automaton $A$
-%has executed the trace $t$.
-\[X \in \bot_{A}(t) \Leftrightarrow \{\exists s.
-s_0  \xrightarrowdbl{t} s \wedge \forall a \in X.
-s \not{\xrightarrow{a}}    \}\] and replace deadlock reducing, under (3) by
-%\[\forall t \in \mathcal{T}_{A_1} \cap  \mathcal{T}_{A_2},\, \bot_{A_2}(t) \subseteq  \bot_{A_1}(t)  \] } 
-%
-%\TODO{thm: backward compatibility + simulation is equivalent to extension refinement in case there is no hole and no guard, i.e. in case the definitions of automata coincide}
-
-\begin{property}[Tracked holes] By construction, if an automaton is the simulation of another one, it is also a simulation by tracking less holes.
-\[\wrel{A_1}{A_2}{H} \land H'\subseteq H \implies \wrel{A_1}{A_2}{H'}\]
-\end{property}
-
-Now that we have a simulation relation that takes both variable parameters and process parameters into account, we would like to ensure that it has  properties one would expect for a simulation relation.
-
-\section{Properties of our Simulation Relations}\label{sec:prop}
+\subsection{Properties}
 
 We now  state the properties of our simulation, proofs of the properties can be found in the appendices.
-We express these properties in terms of hole-tracking simulation because, thanks to Property~\ref{lem-sim-sim}   all the properties  of hole-tracking simulation are also valid  for hole-equal simulation
+We express these properties in terms of hole-tracking simulation because, thanks to Property~\ref{lem-sim-sim}   all the properties  of hole-tracking simulation are also valid  for hole-equal simulation.
 The first crucial property of  simulation  is that it is  a  preorder on the set of OA. This property enables stepwise refinement.
@@
 We then prove that this relation  is a simulation, according to Definition~\ref{Def:OA-Refinement}.
-
 \end{proofsketch}
@@
 The origins of the simulation are in the  approach of programming that aims to provide solid foundations for building correct programs \cite{Dijkstra76}.
-There many work that contributed to the further development of the refinement calculus in various area (e.g.
+Many work  contributed to the  development of the refinement calculus \LUDO{TODO: define refinement calculus} in various area (e.g.
 \cite{BACK1990133,Abrialbooks96,soton250550,Bellegarde:2000}).
-However, the work focused on the analysis and applicability of refinement to systems that are inherently closed, i.e., systems which is bounded and without environment,
-
-There is not a lot of works that has focused on  the refinement of open systems. Defining refinement of open systems as trace inclusion  is  addressed  as a notion of subtyping in type theory 
+However, these works focused on the analysis and applicability of refinement to systems that are inherently closed, i.e., systems which are bounded and without environment,
+
+There are not a lot of works that study refinement for open systems. Defining refinement of open systems as trace inclusion  is  addressed  as a notion of subtyping in type theory 
 \cite{GayH:2005,BravettiZ:2021}.
-This kind of refinement is  based  on interface-oriented approach, it allows the expression of more internal choices and less external choices.
-The refinement of open systems is also defined in terms of  alternating simulation \cite{Alur:1998,deAlfaro:2021}, which deals with game-based models.
-Alternating simulation that is originating from the game theory \cite{deAlfaro:2003} allows  the study of relation between individual components by viewing them as alternating transition systems.
+This kind of refinement is  based  on an interface-oriented approach, it allows the expression of more\Ludo{more and lesss than what???} internal choices and less external choices.
+The refinement of open systems is also defined in terms of  alternating simulation \cite{Alur:1998,deAlfaro:2021}.
+Alternating simulation  is originating from the game theory \cite{deAlfaro:2003}, it allows  the study of relation between individual components by viewing them as alternating transition systems.
 In particular,  a refinement of game-based automata expresses that the refined component can offer more services (input actions) and fewer service demands (output actions).
@@
 The theory of alternating simulation provides an optimistic approach to compute compatibility between automata based on the fact that each automaton expects the other to provide  legal inputs, i.e, two components can be composed if there is an environment where they can work together.
-As we shall see in this paper,
-our approach to design simulation  has some commonalities with that of the above mentioned \cite{deAlfaro:2021}: both are process-oriented approach even if they are not based on the same notion of simulation and they are based on optimistic approach to composition.
-For the composability, we use the notion of comparability of holes (similar to the notion of compatibility), which is explicitly encompassed in the definition of composition.
+Our approach  has some commonalities with  the above mentioned simulation \cite{deAlfaro:2021}: both are process-oriented approaches even if they are not based on the same notion of simulation and both are based on optimistic approach to composition\LUDO{we should explain that we are optimistic, then}.
+For the composability, we use the notion of comparability of holes \LUDO{do we? where?} (similar to the notion of compatibility), which is explicitly encompassed in the definition of composition.
 
 Previous works on OA focused on equivalence relations compatible with composition.
-In  \cite{10.1145/3372884.3373161}, a computable bisimulation is introduced, while in \cite{AMHEEMA:2023} is introduced a weak version of the bisimulation on OA. 
+In  \cite{10.1145/3372884.3373161}, a computable bisimulation is introduced, while in \cite{AMHEEMA:2023}  a weak version of the bisimulation is introduced. 
 In this paper we tackle the refinement relation in the form of simulation, as is the case for the corresponding relations on labelled transition systems \cite{Bellegarde:2000}.
-But unlike the standard simulation we deal with symbolic and open models.
+Unlike the standard simulation we deal with symbolic and open models.
 In \cite{Zhang2014}, the authors exploit transition systems to reason about the systems  that are partially specified by using variables, making  the state space potentially infinite.
@@
 safety properties as deadlock-freeness  and, more generally, 
-all linear temporal logic properties.
+all linear temporal logic properties \LUDO{add ref!}.
 Our focus is about the properties of simulation, in particular closure properties such as preservation under composition.
 Some works   have addressed the problem of non-introduction of blocking by composition.
-For example, in \cite{DIHEGO2020110598} it is presented a refinement relation on process algebra based on failure semantics that is basically different from the (bi)simulation \cite{10.5555/640428.640430}.
+For example,  \cite{DIHEGO2020110598}  presented a refinement relation on process algebra based on failure semantics that is basically different from the (bi)simulation \cite{10.5555/640428.640430}.
+\LUDO{the last sentence is not really informative} \LUDO{how do we compare our work?}
 

### 2023-06-19 2021-Refinement/paper/refinementarticleV2.tex
TODOS

@@
 \cite{GayH:2005,BravettiZ:2021}.
-This kind of refinement is  based  on an interface-oriented approach, it allows the expression of more\Ludo{more and lesss than what???} internal choices and less external choices.
+This kind of refinement is  based  on an interface-oriented approach, it allows the expression of more\LUDO{more and lesss than what???} internal choices and less external choices.
 The refinement of open systems is also defined in terms of  alternating simulation \cite{Alur:1998,deAlfaro:2021}.

### 2023-06-19 2021-Refinement/paper/refinementarticleV2.tex
abstract

@@
 verifying their correctness. By establishing that the
-behaviours of a modified program simulate those of the source one, bisimulation relations formalise the desired relation between a specification and an implementation, 
+behaviours of a modified program simulate those of the source one, simulation relations formalise the desired relation between a specification and an implementation, 
  two equivalent implementations, or a program and its optimised implementation.
-This article discusses a notion of refinement between \emph{open automata}, which are symbolic
+This article discusses a notion of simulation between \emph{open automata}, which are symbolic
 behavioural models for communicating systems. 
@@
 
-We define refinement relations between systems including either equal or different sets of holes, and 
+We define a simulation between open automata that may or may not have the same holes, and 
 show under which conditions these refinements are preserved by composition of open automata.

### 2023-06-20 2021-Refinement/paper/refinementarticleV2.tex
relectire

@@
 The refinement concept also plays  an important role in software engineering.
-In addition to helping to cope with the complexity \LUDO{of what?}, refinement provides a foundation for ensuring  system (software) correctness.
+In addition to helping to cope with the complexity of requirements and design \LUDO{\st{of what?}}, refinement provides a foundation for ensuring  system (software) correctness.
 The correctness of a system can
@@
 From a formal point of view,  refinement can be defined as a mathematical relations between a specification and its implementation, one frequently used relation is trace inclusion or simulation  \cite{Milner:1980,Kouchnarenko:2007}.
-Each \LUDO{each what?} offers specific guarantees on the  behavioural properties of the specification, and it \LUDO{what is ``it''?} ensures that all behaviours of the specification must belong to the behaviours of the implementation.
-This definition \LUDO{which definition?}, which is based on systems whose behaviour is fully defined, is not well-suited for open systems,  as it requires to reason also about unspecified behaviours.
+Each semantic treatment \LUDO{\st{each what?}} offers specific guarantees on the  behavioural properties of the specification, and it \LUDO{what is ``it''?} ensures that all behaviours of the specification must belong to the behaviours of the implementation.
+This refinement semantics is  used to study the behaviour of  closed
+systems \LUDO{\st{which definition?}}, i.e.  systems whose behaviour is fully defined. It is not well-suited for open systems,  as it requires to reason also about unspecified behaviours.
 
@@
 \cite{BACK1990133,Abrialbooks96,soton250550,Bellegarde:2000}).
+\RAB{This development approach is primarily concerned with  whether a program is correct with respect to given properties, and how to improve (refine) a program while preserving its correctness.}
  However, these works focused on the analysis and applicability of refinement to systems that are inherently closed, i.e., systems which are bounded and without environment,

### 2023-06-20 2021-Refinement/paper/refinementarticleV2.tex
meeting

@@
 
-\keywords{Labelled transition systems  \and Refinement \and Composition.}
+\keywords{Labelled transition systems  \and Refinement \and simulation \and Composition.}
 \end{abstract}
@@
 		\quad \mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H} \nwedge\\[1pt]
-		 V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\\hspace{5em} \mpar{R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+		 V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\\hspace{5em} \mpar{\mathcal{R}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
 			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}   \nwedge\\
@@
 $A_{23}$) the OA resulting from $A_1\subst{A_3}{k}$ (resp.
-$A_2\subst{A_3}{k}$),  to prove the theorem it is sufficient to prove that there exists a relation between states of the two OA that satisfies the conditions of the Definition \ref{Def:OA-Refinement}.
+$A_2\subst{A_3}{k}$),  to prove the theorem it is sufficient to prove that there exists a relation between states of the two OA that satisfies the conditions of  Definition~\ref{Def:OA-Refinement}.
 
@@
 &=((J'_{3x}\cap (H\uplus J_1))\uplus (J^{2 \prime}_{1}\cap (H\uplus J_1)))\setminus \mbrc{k}\\
-&=((J'_{3x}\cap H)\uplus (J^{2 \prime}_{1}\cap  J_1))\setminus \mbrc{k}\text{ since } J_1\cap J'_{3x} = \emptyset \text{ and } H\cap J^{2 \prime}_{1} = \emptyset\\
+&=((J'_{3x}\cap H)\uplus (J^{2 \prime}_{1}\cap  J_1))\setminus \mbrc{k}\\
+& \qquad\qquad\qquad\qquad\text{ since } J_1\cap J'_{3x} = \emptyset \text{ and } H\cap J^{2 \prime}_{1} = \emptyset\\
 & =((J'_{3x}\cap H)\uplus J^{2 \prime}_{1})\setminus \mbrc{k}\text{ since } J^{2 \prime}_{1}\subseteq J_1\\
 & =((J'_2\cap H)\uplus J^{1 \prime}_{1})\setminus \mbrc{k}\\
-& \qquad\qquad\qquad \text{ since } J^{1 \prime}_{1}=J^{2 \prime}_{1} \text{ and } J'_2 \cap H = J'_{3x} \cap H\\
+& \qquad\qquad\qquad\qquad \text{ since } J^{1 \prime}_{1}=J^{2 \prime}_{1} \text{ and } J'_2 \cap H = J'_{3x} \cap H\\
 &= ((J'_2 \cap H) \uplus (J^{1 \prime}_{1} \cap J_1)) \setminus \mbrc{k}\text{ since } J^{1 \prime}_{1}\subseteq J_1\\ 
-& = (J'_2\cap (J_1 \uplus H)) \uplus ((J^{1 \prime}_{1} \cap (J_1 \uplus H)) \setminus \mbrc{k} \text{ since } J_1\cap J'_{2} = \emptyset \text{ and } H\cap J^{1 \prime}_{1} = \emptyset\\
+& = (J'_2\cap (J_1 \uplus H)) \uplus ((J^{1 \prime}_{1} \cap (J_1 \uplus H)) \setminus \mbrc{k}\\
+& \qquad\qquad\qquad\qquad \text{ since } J_1\cap J'_{2} = \emptyset \text{ and } H\cap J^{1 \prime}_{1} = \emptyset\\
 		& = \mpar{(J'_2  \uplus J^{1 \prime}_{1})\setminus \mbrc{k}} \cap \mpar{(J_{1} \uplus H) \setminus \mbrc{k}}\\
@@
 We compose by disjunction with the following hypothesis (part of formula $(*)$).\\ $V_{2} \uplus V_{3} \uplus \fvars{t_2}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj}}$
-\begin{align*}
+\begin{align*}\hspace{-5ex}
  V_{2} \uplus V_{3}  \uplus V^1_{1} \uplus V^2_{1} \uplus \fvars{t_{12}}\vdash &    \bigwedge_\subbox{v_1\in V_1}\!\!

### 2023-06-21 2021-Refinement/paper/refinementarticleV2.tex
minor

@@
 More precisely, we define a relation of the following form:
-  \[\mathcal{R}_{13}(s_1,s_3)=\bigvee_{s_2\in S_2}\mpar{\mathcal{R}_{12}(s_1,s_2) \land R_{23}(s_2,s_3) } \]
+  \[\mathcal{R}_{13}(s_1,s_3)=\bigvee_{s_2\in S_2}\mpar{\mathcal{R}_{12}(s_1,s_2) \land \mathcal{R}_{23}(s_2,s_3) } \]
 We then prove that this relation  is a simulation, according to Definition~\ref{Def:OA-Refinement}.

### 2023-06-21 2021-Refinement/paper/refinementarticleV2.tex
in progress

--- 2023-06-20 2021-Refinement/paper/refinementarticleV2.tex
@@
 
-\keywords{Labelled transition systems  \and Refinement \and simulation \and Composition.}
+\keywords{Labelled transition systems  \and Refinement \and Simulation \and Composition.}
 \end{abstract}
@@
 Automata are often used as the basic formalism for this approach, but most automata definitions allow only the specifications of finite closed systems.
-Indeed those systems are the ones we can verify efficiently, but programming often consists in writing open systems that should be interfaced with others, and with potentially unbound behaviours (at least statically).
+Indeed, those systems are the ones we can verify efficiently, but programming often consists in writing open systems that should be interfaced with others, and with potentially unbound behaviours (at least statically).
 We investigate in our works the possibility to define open symbolic systems, verify some of their properties, and use them to compose in a structured way more complex systems.
@@
 The refinement concept also plays  an important role in software engineering.
-In addition to helping to cope with the complexity of requirements and design \LUDO{\st{of what?}}, refinement provides a foundation for ensuring  system (software) correctness.
+In addition to helping to cope with the complexity of requirements and design, refinement provides a foundation for ensuring  system (software) correctness.
 The correctness of a system can
@@
 From a formal point of view,  refinement can be defined as a mathematical relations between a specification and its implementation, one frequently used relation is trace inclusion or simulation  \cite{Milner:1980,Kouchnarenko:2007}.
-Each semantic treatment \LUDO{\st{each what?}} offers specific guarantees on the  behavioural properties of the specification, and it \LUDO{what is ``it''?} ensures that all behaviours of the specification must belong to the behaviours of the implementation.
-This refinement semantics is  used to study the behaviour of  closed
+\RAB{The refinement approach provides mechanism for transforming high-level processes into concrete processes (i.e.
+implementation), in such a way that some behavioural properties are preserved within the transformation.} \st{semantic treatment  offers specific guarantees on the  behavioural properties of the specification, and it ensures that all behaviours of the specification must belong to the behaviours of the implementation.} Most  refinement work focused on  the study  of  closed
 systems \LUDO{\st{which definition?}}, i.e.  systems whose behaviour is fully defined. It is not well-suited for open systems,  as it requires to reason also about unspecified behaviours.
 
-Open automata (that we abbreviate OA) were defined as a way to provide a semantics for open parameterized hierarchical labelled transition systems (abbreviated LTS).
-They were proposed as a theoretical foundation for parametrised automatas used in verification tools and called \emph{pNets}.
+Open automata (that we abbreviate OA) were defined as a way to provide a semantics for open parameterised hierarchical labelled transition systems (abbreviated LTS).
+They were proposed as a theoretical foundation for parametrised automata used in verification tools and called \emph{pNets}.
 An OA \cite{henrio:01299562} is similar to a classical automaton but with variables and holes.
@@
 
-In previous works \cite{AMHEEMA:2023,wang:03126313} a bisimulation relation was defined for OA and open parameterized hierarchical LTSs.
+In previous works \cite{AMHEEMA:2023,wang:03126313} a bisimulation relation was defined for OA and open parameterised hierarchical LTSs.
 It has already good properties relatively to bisimulation, but refinement relations were not studied.
@@
 Our definition captures a simple simulation for OA with the same holes that is more expressive than a strict simulation since it matches a transition with a family of transitions. 
-For example,
-With such a relation we are able to check the simulation between two OA that differ by duplicated states, removed duplicated transitions,  reinforced  guards, different variables, etc.
+For example, with such a relation we are able to check the simulation between two OA that differ by duplicated states, removed duplicated transitions,  reinforced  guards, different variables, etc.
 We will show in Section~\ref{sec:prop} that this simulation relation has good properties in terms of transitivity, compositionality, and reflexivity.
@@
 The way we solve this issue is to remember in the simulation relation which holes have been compared.
-This makes the relation parameterized by a subset of the set of holes that belong to the two automata that we want to take into account.
+This makes the relation parameterised by a subset of the set of holes that belong to the two automata that we want to take into account.
 This way, in the example above, we would have no guarantee on actions the hole $j$ by transitivity but can state a simulation relation with guarantees on the actions of the other holes.
@@
 
-The origins of the simulation are in the  approach of programming that aims to provide solid foundations for building correct programs \cite{Dijkstra76}.
-Many work  contributed to the  development of the refinement calculus \LUDO{TODO: define refinement calculus} in various area (e.g.
+The origins of refinement are in the  approach of programming that aims to provide solid foundations for building correct programs \cite{Dijkstra76}.
+Many work  contributed to the  development of elaborated notions of refinement \LUDO{\st{TODO: define refinement calculus}} in various area (e.g.
 \cite{BACK1990133,Abrialbooks96,soton250550,Bellegarde:2000}).
-\RAB{This development approach is primarily concerned with  whether a program is correct with respect to given properties, and how to improve (refine) a program while preserving its correctness.}
+
  However, these works focused on the analysis and applicability of refinement to systems that are inherently closed, i.e., systems which are bounded and without environment,
@@
 safety properties as deadlock-freeness  and, more generally, 
-all linear temporal logic properties \LUDO{add ref!}.
+all linear temporal logic properties \cite{Manna:1992} \LUDO{\st{add ref!}}.
 Our focus is about the properties of simulation, in particular closure properties such as preservation under composition.
@@
 It relies on a simulation relation between the two automata;  it  specifies that the refined process must follow the behaviour of the simulated one.
-We finally showed that simulation is a preorder that is preserved by composition, both when filling a hole and when placing auomata in comparable contexts.
+We finally showed that simulation is a preorder that is preserved by composition, both when filling a hole and when placing automata in comparable contexts.
 

### 2023-06-21 2021-Refinement/paper/refinementarticleV2.tex
few adds....

@@
 \cite{BACK1990133,Abrialbooks96,soton250550,Bellegarde:2000}).
-
- However, these works focused on the analysis and applicability of refinement to systems that are inherently closed, i.e., systems which are bounded and without environment,
+In the context of process algebra, refinement between processes can be defined in terms of simulations relation (e.g.
+(\cite{Jifeng:1089,Milner:1980}).
+However, the concept of simulations presented so far has focused on the refinement of systems that are inherently closed, i.e., systems which are bounded and without environment,
 
@@
 The theory of alternating simulation provides an optimistic approach to compute compatibility between automata based on the fact that each automaton expects the other to provide  legal inputs, i.e, two components can be composed if there is an environment where they can work together.
-Our approach  has some commonalities with  the above mentioned simulation \cite{deAlfaro:2021}: both are process-oriented approaches even if they are not based on the same notion of simulation and both are based on optimistic approach to composition\LUDO{we should explain that we are optimistic, then}.
+Our approach  has some commonalities with  the above mentioned simulation \cite{deAlfaro:2021}: both are process-oriented approaches even if they are not based on the same notion of simulation and both are based on optimistic approach to composition.
+Rather than being prepared to cope with all environments, components are described together with the environment with which they will interact.
+\LUDO{\st{we should explain that we are optimistic, then}}.
+They
 For the composability, we use the notion of comparability of holes \LUDO{do we? where?} (similar to the notion of compatibility), which is explicitly encompassed in the definition of composition.

### 2023-06-22 2021-Refinement/paper/refinementarticleV2.tex
intro???

@@
 From a formal point of view,  refinement can be defined as a mathematical relations between a specification and its implementation, one frequently used relation is trace inclusion or simulation  \cite{Milner:1980,Kouchnarenko:2007}.
-\RAB{The refinement approach provides mechanism for transforming high-level processes into concrete processes (i.e.
-implementation), in such a way that some behavioural properties are preserved within the transformation.} \st{semantic treatment  offers specific guarantees on the  behavioural properties of the specification, and it ensures that all behaviours of the specification must belong to the behaviours of the implementation.} Most  refinement work focused on  the study  of  closed
-systems \LUDO{\st{which definition?}}, i.e.  systems whose behaviour is fully defined. It is not well-suited for open systems,  as it requires to reason also about unspecified behaviours.
+Refinement is an approach that specifies how to transform an abstract or coarse-grain specification of a process into a concrete finer grain view of this process while maintaining some desirable properties.
+Most  refinement work focused on  the study  of  closed
+systems , i.e.  systems whose behaviour is fully defined. \LUDO{revoir la fin a mon avis: si on veut se distinguer des travaux composants, il faut expliquer} 
+However, adopting a refinement approach in an open system that will later interact 
+It is not well-suited for open systems,  as it requires to reason also about unspecified behaviours.
 

### 2023-06-22 2021-Refinement/paper/refinementarticleV2.tex
iteration on comments

@@
 The origins of refinement are in the  approach of programming that aims to provide solid foundations for building correct programs \cite{Dijkstra76}.
-Many work  contributed to the  development of elaborated notions of refinement \LUDO{\st{TODO: define refinement calculus}} in various area (e.g.
+Many work  contributed to the  development of elaborated notions of refinement  in various area (e.g.
 \cite{BACK1990133,Abrialbooks96,soton250550,Bellegarde:2000}).
@@
 Rather than being prepared to cope with all environments, components are described together with the environment with which they will interact.
-\LUDO{\st{we should explain that we are optimistic, then}}.
+\LUDO{\st{we should explain that we are optimistic, then}} \LUDO{Je comprends pas l argument: ca a l air de dire qu on fait pas des systemes ouverts.
+en effet dans ce papier on decrit pas l environnement dans ce travail, a ce que je comprends?
+A REVOIR}.
 They
@@
 safety properties as deadlock-freeness  and, more generally, 
-all linear temporal logic properties \cite{Manna:1992} \LUDO{\st{add ref!}}.
+all linear temporal logic properties \cite{Manna:1992} \LUDO{\st{add ref!}} \LUDO{add ref sur ``simulation  ensures the preservation of  safety properties'' pas sur temporal logic!}.
 Our focus is about the properties of simulation, in particular closure properties such as preservation under composition.

### 2023-06-22 2021-Refinement/paper/refinementarticleV2.tex
intro

@@
  \and
-INRIA Sophia Antipolis M\'edit\'erann\'ee, UCA,  France
+INRIA Sophia Antipolis M\'edit\'erann\'ee, UCA,  France\\
 \email{first.last@inria.fr}}
@@
 
+\RAB{Skeleton-based systems, such as skeleton-based parallel programs, consist of  a collection of high-level patterns with parallel semantics,  but also provide a systematic way of developing practical programs.
+Skeleton specification is refined by applying a sequence of transformation rules until implementation.
+In this high-level parallel design  approach, each skeleton is a parametric process, it accepts as a parameter the kind of computation to be performed according to the behaviour it models.
+}
+
 The refinement concept also plays  an important role in software engineering.
@@
 Refinement is an approach that specifies how to transform an abstract or coarse-grain specification of a process into a concrete finer grain view of this process while maintaining some desirable properties.
-Most  refinement work focused on  the study  of  closed
-systems , i.e.  systems whose behaviour is fully defined. \LUDO{revoir la fin a mon avis: si on veut se distinguer des travaux composants, il faut expliquer} 
+\RAB{Most  refinement work focused on  the study  of  systems whose behaviour is fully defined.}
+
+\LUDO{revoir la fin a mon avis: si on veut se distinguer des travaux composants, il faut expliquer} 
 However, adopting a refinement approach in an open system that will later interact 

### 2023-06-23 2021-Refinement/paper/refinementarticleV2.tex
correction

@@
 
-\RAB{Skeleton-based systems, such as skeleton-based parallel programs, consist of  a collection of high-level patterns with parallel semantics,  but also provide a systematic way of developing practical programs.
+\RAB{Many parallel programs  such as skeleton-based parallel programs,  can be characterized  by a collection of high-level patterns with parallel semantics,  but also provide a systematic way of developing practical programs.
 Skeleton specification is refined by applying a sequence of transformation rules until implementation.
@@
 There are not a lot of works that study refinement for open systems. Defining refinement of open systems as trace inclusion  is  addressed  as a notion of subtyping in type theory 
-\cite{GayH:2005,BravettiZ:2021}.
-This kind of refinement is  based  on an interface-oriented approach, it allows the expression of more\LUDO{more and lesss than what???} internal choices and less external choices.
+(e.g. \cite{GayH:2005,BravettiZ:2021}). The definition of refinement is based on a connection  between session types and communicating automata theories -- a notion of session automata
+based on Communicating Finite-State Machines, that are used for  modelling processes communicating through FIFO channels.
+\LUDO{\st{more and lesss than what???}}.
 The refinement of open systems is also defined in terms of  alternating simulation \cite{Alur:1998,deAlfaro:2021}.
@@
 safety properties as deadlock-freeness  and, more generally, 
-all linear temporal logic properties \cite{Manna:1992} \LUDO{\st{add ref!}} \LUDO{add ref sur ``simulation  ensures the preservation of  safety properties'' pas sur temporal logic!}.
+all linear temporal logic properties in the sense of \cite{Abrialbooks96,Kouchnarenko:2007} \LUDO{\st{add ref sur ``simulation  ensures the preservation of  safety properties'' pas sur temporal logic!}}.
 Our focus is about the properties of simulation, in particular closure properties such as preservation under composition.

### 2023-06-23 2021-Refinement/paper/refinementarticleV2.tex
ref

@@
 safety properties as deadlock-freeness  and, more generally, 
-all linear temporal logic properties in the sense of \cite{Abrialbooks96,Kouchnarenko:2007} \LUDO{\st{add ref sur ``simulation  ensures the preservation of  safety properties'' pas sur temporal logic!}}.
+all linear temporal logic properties \cite{Abrialbooks96,Kouchnarenko:2007}.
 Our focus is about the properties of simulation, in particular closure properties such as preservation under composition.

### 2023-06-23 2021-Refinement/paper/refinementarticleV2.tex
minor
An intro

@@
 \usepackage{cancel}
+
+\usepackage{paralist}
 \AtBeginDocument{\renewcommand\setminus{\smallsetminus}}
@@
 
-\keywords{Labelled transition systems  \and Refinement \and Simulation \and Composition.}
+\keywords{Labelled transition systems   \and Simulation \and Composition.}
 \end{abstract}
@@
 %* global rewriting (partly done)
+
+% we do compositional reasoning on systems
  Compositional design is a highly convenient approach 
@@
 Automata are often used as the basic formalism for this approach, but most automata definitions allow only the specifications of finite closed systems.
-Indeed, those systems are the ones we can verify efficiently, but programming often consists in writing open systems that should be interfaced with others, and with potentially unbound behaviours (at least statically).
-We investigate in our works the possibility to define open symbolic systems, verify some of their properties, and use them to compose in a structured way more complex systems.
-
-\RAB{Many parallel programs  such as skeleton-based parallel programs,  can be characterized  by a collection of high-level patterns with parallel semantics,  but also provide a systematic way of developing practical programs.
-Skeleton specification is refined by applying a sequence of transformation rules until implementation.
-In this high-level parallel design  approach, each skeleton is a parametric process, it accepts as a parameter the kind of computation to be performed according to the behaviour it models.
-}
-
-The refinement concept also plays  an important role in software engineering.
-In addition to helping to cope with the complexity of requirements and design, refinement provides a foundation for ensuring  system (software) correctness.
+These systems  can be verified efficiently, but programming often consists in writing  systems that should be interfaced with others, and with potentially unbound behaviours.
+We investigate in our works the reasoning on open symbolic systems, with a strong focus on compositionality of properties.
+More precisely, we say that a system is open if it contains a ``hole'' to be filled by another system.
+Open systems are typically composition operators~\cite{henrio:01299562} or componentised systems where some of the components are yet to be provided~\cite{AMHEEMA:2023}.
+This form of composition is more complex to handle than top-level interaction usually found in process algebra, as the behaviour of each entity in the system is parameterised both by classical symbolic variables and by process variables.
+
+% why refinement
+The refinement concept  plays  an important role in software engineering.
+In addition to helping to cope with the complexity of requirements and design, refinement provides a foundation for ensuring  system  correctness.
 The correctness of a system can
-be established by proving, that a system refines its specification.
-%Refinement relations verify that an implementation satisfies some properties with respect to a specification. 
+be established by proving, that a system refines its specification with the idea that some properties of the specification are preserved in the refined system.
 Refinement entails that one system  can be considered as a more precise version of another one that is considered to be the specification.
 The refined model features all the specified behaviours with more concrete details.
-From a formal point of view,  refinement can be defined as a mathematical relations between a specification and its implementation, one frequently used relation is trace inclusion or simulation  \cite{Milner:1980,Kouchnarenko:2007}.
-Refinement is an approach that specifies how to transform an abstract or coarse-grain specification of a process into a concrete finer grain view of this process while maintaining some desirable properties.
-\RAB{Most  refinement work focused on  the study  of  systems whose behaviour is fully defined.}
-
-\LUDO{revoir la fin a mon avis: si on veut se distinguer des travaux composants, il faut expliquer} 
-However, adopting a refinement approach in an open system that will later interact 
-It is not well-suited for open systems,  as it requires to reason also about unspecified behaviours.
-
+From a formal point of view,  refinement is a mathematical relations between a specification and its implementation, one frequently used relation is trace inclusion or simulation  \cite{Milner:1980,Kouchnarenko:2007}.
+
+% objective: a simulation theory for open systems
+In this article, we design a simulation theory for open symbolic systems.
+We build a very generic theory that should allow us to reason on simulation-based verification for most concurrent systems, as our base theory merely relies on automata parameterised by both variables and processes.
+As we shall see, our composition of automata is also very generic to account for any interaction mechanism found in concurrent systems.
+While our contribution is theoretical, it establishes the foundations for to the verification of any compositionally designed system, like  component systems, algorithmic skeletons.
+
+% OA
 Open automata (that we abbreviate OA) were defined as a way to provide a semantics for open parameterised hierarchical labelled transition systems (abbreviated LTS).
@@
  of the main automaton has been provided.
+Because of their the generic nature, the notion of OA model is quite abstract but we already illustrated previously how to derive OAs for process algebra operators~\cite{henrio:01299562} or for component systems~\cite{AMHEEMA:2023,ameurboulifa:01526055}.
 
@@
 Our contribution in this paper is the definition a simulation relation for OA that has the following characteristics:
-\begin{itemize}
+\begin{compactitem}
 \item Classical simulation characterisation but also an additional criteria ensuring that simulation does not introduce deadlocks when following a trace from the simulated automaton.
@@
 \item Ability to take into account both composition and transitivity: this is a challenge because composition changes the set of holes of the OA and simulation takes into account the actions of the holes.
-\end{itemize}
+\end{compactitem}
  The simulation relation is introduced in two steps.
@@
 based on Communicating Finite-State Machines, that are used for  modelling processes communicating through FIFO channels.
-\LUDO{\st{more and lesss than what???}}.
 The refinement of open systems is also defined in terms of  alternating simulation \cite{Alur:1998,deAlfaro:2021}.
@@
 Rather than being prepared to cope with all environments, components are described together with the environment with which they will interact.
-\LUDO{\st{we should explain that we are optimistic, then}} \LUDO{Je comprends pas l argument: ca a l air de dire qu on fait pas des systemes ouverts.
+\LUDO{Je comprends pas l argument: ca a l air de dire qu on fait pas des systemes ouverts.
 en effet dans ce papier on decrit pas l environnement dans ce travail, a ce que je comprends?
@@
 
-In the future, we will investigate under which condition, the composition operation produces a refinement in the sense that filling a hole produces a refined process.
+%In the future, we want to investigate under which condition, the composition operation produces a refinement in the sense that filling a hole produces a refined process.
 

### 2023-06-23 2021-Refinement/paper/refinementarticleV2.tex
my change

@@
 The theory of alternating simulation provides an optimistic approach to compute compatibility between automata based on the fact that each automaton expects the other to provide  legal inputs, i.e, two components can be composed if there is an environment where they can work together.
-Our approach  has some commonalities with  the above mentioned simulation \cite{deAlfaro:2021}: both are process-oriented approaches even if they are not based on the same notion of simulation and both are based on optimistic approach to composition.
-Rather than being prepared to cope with all environments, components are described together with the environment with which they will interact.
-\LUDO{Je comprends pas l argument: ca a l air de dire qu on fait pas des systemes ouverts.
+Our approach  has some commonalities with  the above mentioned simulation \cite{deAlfaro:2021}: both are process-oriented approaches even if they are not based on the same notion of simulation, and both include in the model  how to compose and interact with processes that are accepted as parameters.
+ \LUDO{\st{Je comprends pas l argument: ca a l air de dire qu on fait pas des systemes ouverts.
 en effet dans ce papier on decrit pas l environnement dans ce travail, a ce que je comprends?
-A REVOIR}.
-They
-For the composability, we use the notion of comparability of holes \LUDO{do we? where?} (similar to the notion of compatibility), which is explicitly encompassed in the definition of composition.
+A REVOIR}}.
 
@@
 For example,  \cite{DIHEGO2020110598}  presented a refinement relation on process algebra based on failure semantics that is basically different from the (bi)simulation \cite{10.5555/640428.640430}.
-\LUDO{the last sentence is not really informative} \LUDO{how do we compare our work?}
+Indeed, failure semantics is based  on a notion of decorated traces.
+Consequently, in this semantics,  refinement is defined in terms of inclusions between their decorated traces,  rather than by simulation.
+\LUDO{\st{the last sentence is not really informative}} \LUDO{\st{how do we compare our work?}}
 
@@
 
-\item \TODO{Ref to JLAMP 2023?}
+\item \RAB{To check}
+ Secondly, we need to prove that for any open transition $t_1$ in $T_1$  originating from $s_1$:
+\begin{align*}
+\OTx{1}{}{1}{1} \in \fOT{s_1}
+\end{align*}
+there exists an indexed family of OTs originating from $s_{3}$: 
+\begin{multline*}
+V_1 \uplus  V_3 \uplus \fvars{t_1}
+\vdash\\\hspace{2em}
+\mpar{R_{13}\mpar{s_1, s_3} \wedge g_1 \implies 
+\operatorname*{\bigsymb{\bigvee}}_{z \in Z}
+\mpar{\everymath{\displaystyle}
+\begin{array}{l}
+\alpha_1=\alpha_{3z}\wedge \bigwedge_\subbox{j \in J'_{3z} \cap (H\cap H')} \beta_{1j}=\beta_{3jz} \wedge \\g_{3z}\wedge 
+{R_{12}\mpar{s'_1,s'_{3z}}}\psubst{\psi_1  \uplus \psi_{3z}}
+\end{array}}}
+\end{multline*}	
+\RAB{The proof follows the same principle as the one given in \cite{AMHEEMA:2023}.  It relies on  the fact that one open transition of $A_1$ is simulated by a
+family of open transitions of $A_2$, and one open transition of $A_2$ is simulated by a family of open transitions of $A_3$.
+Transitivity leads to a doubly indexed family of simulating open transition.}
 
@@
 %\everymath{\displaystyle}
-V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\ \mpar{\mathcal{R}\mpar{s_1, s_{2}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
+V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\ \mathcal{R}\mpar{s_1, s_{2}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
 \begin{array}{l}
@@
 			 g_{2x} \wedge \mathcal{R}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}}}  \qquad \quad (*)
+		\end{array}}  \qquad \quad (*)
 \end{multline*}	
@@
 &=((J'_{2x}\cap (H\uplus J_3))\uplus (J^{2 \prime}_{3}\cap (H\uplus J_3)))\setminus \mbrc{k}\\
-&=((J'_{2x}\cap H)\uplus (J^{2 \prime}_{3}\cap  J_3))\setminus \mbrc{k}\text{ since } J_3\cap J'_{2x} = \emptyset \text{ and } H\cap J^{2 \prime}_{3} = \emptyset\\
+&=((J'_{2x}\cap H)\uplus (J^{2 \prime}_{3}\cap  J_3))\setminus \mbrc{k}\\
+& \qquad\qquad\qquad\qquad \text{ since } J_3\cap J'_{2x} = \emptyset \text{ and } H\cap J^{2 \prime}_{3} = \emptyset\\
 & =((J'_{2x}\cap H)\uplus J^{2 \prime}_{3})\setminus \mbrc{k}\text{ since } J^{2 \prime}_{3}\subseteq J_3\\
@@
 &= ((J'_1 \cap H) \uplus (J^{1 \prime}_{3} \cap J_3)) \setminus \mbrc{k}\text{ since } J^{1 \prime}_{3}\subseteq J_3\\ 
-& = (J'_1\cap (J_3 \uplus H)) \uplus ((J^{1 \prime}_{3} \cap (J_3 \uplus H)) \setminus \mbrc{k} \text{ since } J_3\cap J'_{1} = \emptyset \text{ and } H\cap J^{1 \prime}_{3} = \emptyset\\
+& = (J'_1\cap (J_3 \uplus H)) \uplus ((J^{1 \prime}_{3} \cap (J_3 \uplus H)) \setminus \mbrc{k} \\
+& \qquad\qquad\qquad\qquad \text{ since } J_3\cap J'_{1} = \emptyset \text{ and } H\cap J^{1 \prime}_{3} = \emptyset\\
 		& = \mpar{(J'_1  \uplus J^{1 \prime}_{3})\setminus \mbrc{k}} \cap \mpar{(J_{3} \uplus H) \setminus \mbrc{k}}\\
@@
 
-From the two previous formula and by introducing the following tautology\\ $ \mpar{\,\,\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}$, we get: \TODO{faire une jolie equation}
-\begin{multline*}
-V_{13} \uplus V_{23}  \vdash  \underbrace{\mathcal{R}\mpar{s_1, s_2} \wedge \reach{A_{13}}(s_{13}) \land \mpar{\,\,\bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3 \wedge s^1_3=s^2_3}}_{\mathcal{R}^{\prime}(s_{13},s_{23})} \wedge \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})   \\ \implies \left(\neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}) \lor \neg{\reach{A_{13}}(s_{13}) }\right) \land \reach{A_{13}}(s_{13})\\
-\implies \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
+From the two previous formula and by introducing the following tautology\\ $ \mpar{\,\,\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}$, we get: 
+\begin{multline*}
+V_{13} \uplus V_{23}  \vdash \!
+\underbrace{\mathcal{R}\mpar{s_1, s_2}\!
+\wedge \!\reach{A_{13}}(s_{13}) \!\land\!
+\mpar{\,\,\bigwedge_\subbox{v_3\in V_3}  v^1_3\!=\!v^2_3 \wedge s^1_3\!=\!s^2_3}}_{\mathcal{R}^{\prime}(s_{13},s_{23})} \wedge \neg\!\!{\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}}   \\ \implies \left(\,\neg{\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}} \lor \neg{\reach{A_{13}}(s_{13}) }\right) \land \reach{A_{13}}(s_{13})
+\implies \neg\!{\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}}
 \end{multline*}
@@
 \begin{enumerate}
-\item \TODO{I skip it, I think the same as previous theorem}
-
+\item First, we have to prove the relation for initial states:
+\[\sigma_{012} \uplus \sigma_{013} \vdash \mathcal{R}'\mpar{s_{012}, s_{013}}\]
+with $\sigma_{012} = \sigma_{01}^1 \uplus \sigma_{03}$, $\sigma_{013} = \sigma_{01}^2 \uplus \sigma_{03}$, $s_{012}=(s_{01}^1,s_{02})$, and $s_{013}=(s_{01}^2,s_{03})$.\\
+\RAB{The proof of this point is similar to that of Theorem \ref{thm:ContextRefinement}.}
 \item Second, we need to prove for any OT $t_{12}$ in $T_{12}$ originating from $s_{12}$
@@
 
-\TODO{NEW -- a refaire en plus joli}
+%\TODO{NEW -- a refaire en plus joli}
 
@@
 \begin{multline*}
-V_{12} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1}  \vdash 
-\neg{ \bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}}
-\implies \\
-\left(\neg{\reach{A_{12}(s_{12})} }\lor \neg{\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
+V_{12} \uplus\! \biguplus_\subbox{t_1 \in \fOT{s_1}}\! \fvars{t_1}  \vdash 
+\neg\!{ \bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}}
+\!\implies\! \!
+\left(\neg{\reach{A_{12}(s_{12})} }\lor \neg\!{\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
 \right)
@@
 g_1\land g_3 \land g$ with $g_1$ a guard of a transition $t_{1}$ of OT$(s_{1})$.
-Thus 
+Thus have
 \[
@@
 
-Thus we have, as $\mathcal{R}$ contains the reachability of state $s_{12}$:\TODO{faire une jolie equation}
-\begin{multline*}
-V_{12} \uplus V_{13}  \vdash  \mathcal{R}'\mpar{s_{12}, s_{13}} \nwedge  \neg(\bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}) \\
-\implies \reach{A_{12}(s_{12})} \land \left(\neg{\reach{A_{12}(s_{12})} }\lor
-\neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})\right) \\
+Thus we have, as $\mathcal{R}$ contains the reachability of state $s_{12}$:
+\begin{multline*}
+V_{12} \uplus V_{13}  \vdash  \mathcal{R}'\mpar{s_{12}, s_{13}} \nwedge  \neg(\bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}) \implies \\
+ \left(\reach{A_{12}(s_{12})} \land \left(\neg{\reach{A_{12}(s_{12})} }\lor
+\neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})\right) 
 \implies
-\neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})
+\neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})\right)
 \end{multline*}

### 2023-06-23 2021-Refinement/paper/refinementarticleV2.tex
meeting

@@
 
+The simulation  ensures the preservation of   
+safety properties as deadlock-freeness  and, more generally, 
+all linear temporal logic properties \cite{Abrialbooks96,Kouchnarenko:2007}.
+The difference between the existing refinement principles have been studied in \cite{10.5555/640428.640430}, for example the authors explain in what sense failure semantics is different from  (bi)simulation in the compared systems and properties ensured.
+In this paper we particularly focus on the compositionality of simulation-based refinement.
+
 There are not a lot of works that study refinement for open systems. Defining refinement of open systems as trace inclusion  is  addressed  as a notion of subtyping in type theory 
@@
 Our approach  has some commonalities with  the above mentioned simulation \cite{deAlfaro:2021}: both are process-oriented approaches even if they are not based on the same notion of simulation, and both include in the model  how to compose and interact with processes that are accepted as parameters.
- \LUDO{\st{Je comprends pas l argument: ca a l air de dire qu on fait pas des systemes ouverts.
-en effet dans ce papier on decrit pas l environnement dans ce travail, a ce que je comprends?
-A REVOIR}}.
+ \LUDO{TODO: what do we do better . in a different context?}.
 
@@
 
-The simulation  ensures the preservation of   
-safety properties as deadlock-freeness  and, more generally, 
-all linear temporal logic properties \cite{Abrialbooks96,Kouchnarenko:2007}.
-Our focus is about the properties of simulation, in particular closure properties such as preservation under composition.
+\LUDO{rewrite the following, relate non-blocking and the citation, is it the good one}
+\LUDO{add reference to Olga for non blocking but she does not ensure compositionality in a very general sense as we do}
 Some works   have addressed the problem of non-introduction of blocking by composition.
-For example,  \cite{DIHEGO2020110598}  presented a refinement relation on process algebra based on failure semantics that is basically different from the (bi)simulation \cite{10.5555/640428.640430}.
+For example,  \cite{DIHEGO2020110598}  presented a refinement relation on process algebra based on.
 Indeed, failure semantics is based  on a notion of decorated traces.
@@
 $A_{13}$) the OA resulting from $A_1\subst{A_2}{k}$ (resp.
-$A_1\subst{A_3}{k}$),  to prove the theorem it is sufficient to prove that there exists a relation between states of the two OA that satisfies the conditions of the Definition \ref{Def:OA-Refinement}.
+$A_1\subst{A_3}{k}$),  to prove the theorem it is sufficient to prove that there exists a relation between states of the two OA that satisfies the conditions of the Definition~\ref{Def:OA-Refinement}.
 
@@
 g_1\land g_3 \land g$ with $g_1$ a guard of a transition $t_{1}$ of OT$(s_{1})$.
-Thus have
+Thus we have
 \[

### 2023-06-23 2021-Refinement/paper/refinementarticleV2.tex
related works

@@
 Our approach  has some commonalities with  the above mentioned simulation \cite{deAlfaro:2021}: both are process-oriented approaches even if they are not based on the same notion of simulation, and both include in the model  how to compose and interact with processes that are accepted as parameters.
- \LUDO{TODO: what do we do better . in a different context?}.
+Nevertheless, they differ in that our approach focuses on the compositional properties of the simulation, and not to composability.
+ \LUDO{\st{TODO: what do we do better . in a different context?}}.
 
@@
 \LUDO{add reference to Olga for non blocking but she does not ensure compositionality in a very general sense as we do}
-Some works   have addressed the problem of non-introduction of blocking by composition.
-For example,  \cite{DIHEGO2020110598}  presented a refinement relation on process algebra based on.
+
+\RAB{Some work have addressed  the component-based refinement issue with the concern  to preserving the deadlock freedom (e.g.
+\cite{DIHEGO2020110598,Kouchnarenko:2007}).
+These works are not concerned with the theory of open symbolic systems, and therefore not the compositionality  in the sense that we do it.
+}
+
+\TODO{A virer -- For example,  \cite{DIHEGO2020110598}  presented a refinement relation on process algebra based on.
 Indeed, failure semantics is based  on a notion of decorated traces.
-Consequently, in this semantics,  refinement is defined in terms of inclusions between their decorated traces,  rather than by simulation.
-\LUDO{\st{the last sentence is not really informative}} \LUDO{\st{how do we compare our work?}}
+Consequently, in this semantics,  refinement is defined in terms of inclusions between their decorated traces,  rather than by simulation.}
 

### 2023-06-26 2021-Refinement/paper/refinementarticleV2.tex
related works: english + appendix

--- 2023-06-23 2021-Refinement/paper/refinementarticleV2.tex
@@
 Our approach  has some commonalities with  the above mentioned simulation \cite{deAlfaro:2021}: both are process-oriented approaches even if they are not based on the same notion of simulation, and both include in the model  how to compose and interact with processes that are accepted as parameters.
- \LUDO{TODO: what do we do better . in a different context?}.
+Nevertheless, they differ in that our approach focuses on the compositional properties of the simulation, and \LUDO{not on the fact that entities can be composed?}.
+% \LUDO{\st{TODO: what do we do better . in a different context?}}.
 
@@
 
-\LUDO{rewrite the following, relate non-blocking and the citation, is it the good one}
-\LUDO{add reference to Olga for non blocking but she does not ensure compositionality in a very general sense as we do}
-Some works   have addressed the problem of non-introduction of blocking by composition.
-For example,  \cite{DIHEGO2020110598}  presented a refinement relation on process algebra based on.
+%
+%\LUDO{rewrite the following, relate non-blocking and the citation, is it the good one}
+%\LUDO{add reference to Olga for non blocking but she does not ensure compositionality in a very general sense as we do}
+
+\LUDO{Some work target component-based refinement  with the concern  of preserving  deadlock freedom (e.g.
+\cite{DIHEGO2020110598,Kouchnarenko:2007}).
+These works are not concerned with the theory of open symbolic systems, and therefore do not focus on the same modularity as we do, in particular we provide preservation of refinement by composition.
+}
+%
+%\TODO{A virer -- For example,  \cite{DIHEGO2020110598}  presented a refinement relation on process algebra based on.
 Indeed, failure semantics is based  on a notion of decorated traces.
-Consequently, in this semantics,  refinement is defined in terms of inclusions between their decorated traces,  rather than by simulation.
-\LUDO{\st{the last sentence is not really informative}} \LUDO{\st{how do we compare our work?}}
+Consequently, in this semantics,  refinement is defined in terms of inclusions between their decorated traces,  rather than by simulation.}
 
@@
 
-\item \RAB{To check}
+\item 
  Secondly, we need to prove that for any open transition $t_1$ in $T_1$  originating from $s_1$:
@@
 \end{multline*}	
-\RAB{The proof follows the same principle as the one given in \cite{AMHEEMA:2023}.  It relies on  the fact that one open transition of $A_1$ is simulated by a
+\RAB{The proof of this simulation step follows the same principles as the one given in \cite{AMHEEMA:2023} for the proof of transitivity of bisimulation\footnote{In particular, the bisimulation relation exhibited for proving transitivity is the same.}.
+It relies on  the fact that one open transition of $A_1$ is simulated by a
 family of open transitions of $A_2$, and one open transition of $A_2$ is simulated by a family of open transitions of $A_3$.

### 2023-06-26 2021-Refinement/paper/refinementarticleV2.tex
meeting

@@
 Our approach  has some commonalities with  the above mentioned simulation \cite{deAlfaro:2021}: both are process-oriented approaches even if they are not based on the same notion of simulation, and both include in the model  how to compose and interact with processes that are accepted as parameters.
-Nevertheless, they differ in that our approach focuses on the compositional properties of the simulation, and \LUDO{not on the fact that entities can be composed?}.
+Nevertheless, they differ in that our approach focuses on the compositional properties of the simulation, and {not on the fact that entities can be composed}.
 % \LUDO{\st{TODO: what do we do better . in a different context?}}.
@@
 
-\LUDO{Some work target component-based refinement  with the concern  of preserving  deadlock freedom (e.g.
+{Some work target component-based refinement  with the concern  of preserving  deadlock freedom (e.g.
 \cite{DIHEGO2020110598,Kouchnarenko:2007}).

### 2023-06-26 2021-Refinement/paper/refinementarticleV2.tex
figs
improvements

@@
 
-\keywords{Labelled transition systems   \and Simulation \and Composition.}
+\keywords{Labelled transition systems   \and Simulation \and Refinement \and Composition.}
 \end{abstract}
@@
 \(\terms\) and \(\actions\) are term algebras.
-The formulas \(\formulas\) contain at least first order formulas and equality\footnote{Equality does not need to be only syntactic.} over \(\terms\) and \(\actions\). 
+The set of formulas \(\formulas\) contain at least first order formulas and equality\footnote{Equality does not need to be only syntactic.} over \(\terms\) and \(\actions\). 
 %\end{definition}
@@
 The set \(\values\) denotes values which is a subset of closed terms.
-\(\rformulas[V]\) is the set of formulas $f$ that only uses variables in $V$, i.e.
-the formulas such that  \(\fvars{f}\subseteq V\).
+\(\rformulas[V]\) is the set of formulas $f$ that only uses variables in $V$, i.e., the formulas such that  \(\fvars{f}\subseteq V\).
 %The substitution in \(e \in E\) of \(x \in \fvars{e}\) by \(t \in \terms\), is denoted \(e\subst{t}{x}\), and its generalisation to t
@@
 
-The example uses several kinds of data.
-Variable $\texttt{m}$ holds a message (we can leave the message type abstract here).
-We additionally use arrays of messages with a syntax of the form $\texttt{M[l]}$ for array accesses; $\texttt{M}$ is an array of $\texttt{N}$ elements, from $0$ to $\texttt{N}-1$.
-Finally we use addition and modulo operation ($\%$) on integers.
-
 The OA  modelling the behaviour of such a system  using an  unbounded circular/ring buffer is depicted in Fig.
@@
 When any process do its internal computation, it is exposed externally as unobservable action $\tau$.
+
+The example uses several kinds of data.
+Variable $\texttt{m}$ holds a message (we can leave the message type abstract here).
+We additionally use arrays of messages with a syntax of the form $\texttt{M[l]}$ for array accesses; $\texttt{M}$ is an array of $\texttt{N}$ elements, from $0$ to $\texttt{N}-1$.
+Finally we use addition and modulo operation ($\%$) on integers.
+
 \begin{figure}[!tb]
@@
 \ref{Fig:procandcons} shows a producer automaton  and a consumer  automaton that can be used  to fill the holes $\texttt{P}$ and $\texttt{Q}$ of \texttt{prod-cons} defined in Example~\ref{Example:fifo-system}.
- \begin{figure}[!b]
+ \begin{figure}[!t]
  \centering
@@
 
-\begin{figure}[!b]
+\begin{figure}[!t]
  \centering
@@
 %\TODO{C'est etrange, la formulation "the variables they refer to", comme il n'y a plus de variables d'etat... +1}
-The idea is that two states are related depending on the satisfiability of the expression relying their variables i.e., if the variables of the OA verify a certain formula. 
+The idea is that two states are related depending on the satisfiability of the expression relying their variables, i.e., if the variables of the OA verify a certain formula. 
 In other words, to each pair of states is attached a boolean formula that may refer to the  variables of each of the two OA, stating whether the two states are related or not.
@@
 Reachability takes into account all paths, and can over-approximate the reachable configurations. 
-From an automation point of view, finding the most precise reachability predicate for a given automata is not decidable because of the symbolic nature of OA, but only an over-approximation is necessary.
+From an automation point of view, finding the most precise reachability predicate for a given automaton is not decidable because of the symbolic nature of OA, but only an over-approximation is necessary.
 
@@
 We rely on a classical notion of simulation inspired from~\cite{AMHEEMA:2023}.
-The idea is to consider two configurations related by a relation; if one state can do a transition, then the other can do a transition too.
+The idea is to consider two configurations related by a relation; if one state can do a transition, then the other can also make this transition.
 Like for bisimulation, a simulation relation characterises when two states are related, and this  characterisation is expressed as a predicate on the variables of the two automata.
-Simulation defines conditions on a predicate $\mathcal{R}$ such that $\mathcal{R}\mpar{s_1, s_2}$ is a predicate (possibly involving variables of the automata) that is true when the state $s_1$ of $A_1$ refines the state $s_2$ of $A_2$.
+Simulation defines conditions on a relation $\mathcal{R}$ such that $\mathcal{R}\mpar{s_1, s_2}$ is a predicate (possibly involving variables of the automata) that is true when the state $s_1$ of $A_1$ simulates the state $s_2$ of $A_2$.
 
@@
 \begin{example} \label{example:fifo-system-one}
-To illustrate the simulation simulation of OA, we consider a variation on the \texttt{prod-cons} example.
+To illustrate the simulation  of OA, we consider a variation on the \texttt{prod-cons} example.
 Namely,  we suppose that  the two processes  \texttt{P} and  \texttt{Q} communicate through a one-place  buffer.
@@
 We can easily check that this automaton simulates the one of Fig.~\ref{Fig:RefineOA}.
-Indeed, one can see that  $\mathcal{R}=\{(r_0,s_0) \mapsto \texttt{l}=\texttt{f}, (r_0,s_1) \mapsto \texttt{f}=\texttt{l}+1\% \texttt{N} \}$ is  a candidate simulation 
+Indeed, one can see that  $\mathcal{R}=\{(r_0,s_0) \mapsto \texttt{l}=\texttt{f}, (r_0,s_1) \mapsto \texttt{f}=\texttt{l}+1\% \texttt{N} \}$ is  a  simulation 
 relation. It follows that  \texttt{prod-cons} $\leq$ \texttt{simprod-cons}. \qed
@@
 A naive definition of simulation would ensure that only the holes that are identical in the two OA are taken into account in the simulation.
-Unfortunately considering all the common holes does not ensure transitivity of the simulation for the following reason.
+Unfortunately, considering all the common holes does not ensure transitivity of the simulation for the following reason.
 If $A_1$ simulates $A_2$ and $A_2$ simulates $A_3$, and one hole $j$ appears in $A_3$ and in $A_1$ but not in $A_2$ then we have no guarantee on the way $A_1$ and $A_3$ take the actions of this his hole into account, thus  a simulation between and $A_1$ and $A_3$ would require conditions involving actions of the hole $j$ which cannot be ensured.
@@
 \end{property}
-\begin{example} Consider the automata of examples \ref{Example:fifo-system} and \ref{example:fifo-system-one}.
+\begin{example} Consider the automata of Examples \ref{Example:fifo-system} and \ref{example:fifo-system-one}.
 As we saw above, \texttt{prod-cons} $\leq$ \texttt{simprod-cons}, therefore \texttt{prod-cons} $\leq_{\{\texttt{P,Q}\}}$ \texttt{simprod-cons}.
@@
 
-Before reasoning on the properties of simulation. we need to introduce one additional notion that characterizes when the composition of two automata does not introduce new blocked transitions.
+Before reasoning on the properties of simulation. we need to introduce one additional notion that characterises when the composition of two automata does not introduce new blocked transitions.
 
@@
 In general, one would not want to only consider non-blocking composition as it may reveal a bit restrictive, but it is the best necessary condition that can be identified for compositionality of simulation.
-It will be used to prove composition theorems below.
+It will be used to prove composition theorems given below.
 In absence of non-blocking composition, simulation may also be checked specifically for a given composed automaton.
@@
 
-We now  state the properties of our simulation, proofs of the properties can be found in the appendices.
+We now  state the properties of our simulation, their proofs  can be found in the appendices.
 We express these properties  in terms of hole-tracking simulation because, thanks to Property~\ref{lem-sim-sim}   all the properties  of hole-tracking simulation are also valid  for hole-equal simulation.
-The first crucial property of  simulation  is that it is  a  preorder on the set of OA. This property enables stepwise refinement.
-
-\begin{theorem}[Simulation is a preorder]
+The first crucial theorem of  simulation  is that it is  a  preorder on the set of OA. This latter enables stepwise refinement.
+
+\begin{theorem}[Simulation is a preorder]\label{thm:preoder}
 Hole-tracking simulation
@@
 The automaton of \texttt{prod-cons[producer/P]} is shown in Fig.~\ref{Fig:ComposeOA}.
-The automaton resulting  from the composition of  \texttt{Simprod} and \texttt{producer} is bigger and not shown here. \qed
+While the automaton resulting  from the composition of  \texttt{simprod-cons} and \texttt{producer} is bigger and not shown here.
+\qed
 \end{example}
@@
 lead to illegal states, where one automaton issues an output that is not acceptable as input in the other one.
-The theory of alternating simulation provides an optimistic approach to compute compatibility between automata based on the fact that each automaton expects the other to provide  legal inputs, i.e, two components can be composed if there is an environment where they can work together.
+The theory of alternating simulation provides an optimistic approach to compute compatibility between automata based on the fact that each automaton expects the other to provide  legal inputs, i.e., two components can be composed if there is an environment where they can work together.
 Our approach  has some commonalities with  the above mentioned simulation \cite{deAlfaro:2021}: both are process-oriented approaches even if they are not based on the same notion of simulation, and both include in the model  how to compose and interact with processes that are accepted as parameters.
@@
 
-\section{Proof of Transitivity for Refinement}\label{sec:proof-transitivity}
+\section{Proof of Transitivity for Refinement (Theorem~\ref{thm:preoder})}\label{sec:proof-transitivity}
 \begin{quote}
@@
 \end{multline*}	
-\RAB{The proof of this simulation step follows the same principles as the one given in \cite{AMHEEMA:2023} for the proof of transitivity of bisimulation\footnote{In particular, the bisimulation relation exhibited for proving transitivity is the same.}.
+The proof of this simulation step follows the same principles as the one given in \cite{AMHEEMA:2023} for the proof of transitivity of bisimulation\footnote{In particular, the bisimulation relation exhibited for proving transitivity is the same.}.
 It relies on  the fact that one open transition of $A_1$ is simulated by a
 family of open transitions of $A_2$, and one open transition of $A_2$ is simulated by a family of open transitions of $A_3$.
-Transitivity leads to a doubly indexed family of simulating open transition.}
+Transitivity leads to a doubly indexed family of simulating open transition.
 
@@
 
-\section{Proof of Congruence}
+\section{Proof of Congruence (Theorem~\ref{thm:CongurenceRefinement})}
 \begin{quote}
@@
 with $\sigma_{012} = \sigma_{01}^1 \uplus \sigma_{03}$, $\sigma_{013} = \sigma_{01}^2 \uplus \sigma_{03}$, $s_{012}=(s_{01}^1,s_{02})$, and $s_{013}=(s_{01}^2,s_{03})$.\\
-\RAB{The proof of this point is similar to that of Theorem \ref{thm:ContextRefinement}.}
+The proof of this point is similar to that of Theorem \ref{thm:ContextRefinement}.
 \item Second, we need to prove for any OT $t_{12}$ in $T_{12}$ originating from $s_{12}$
@@
 We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (as stated above).
-By hypothesis we have $k \in H$, so in the case where $k \in {J^1_{1}}^{\prime}$, we deduce that $k \in J'_{3x}$ we can  then build  a family of OTs $t_{13x}^{x\in X}$ with the same transition, up to renaming, as the one used to build $t_{12}$ (i.e.
-$t_1^1$), where ${s^2_{1}}^\prime$ is the same as ${s^1_{1}}^\prime$ up to renaming.
+By hypothesis we have $k \in H$, so in the case where $k \in {J^1_{1}}^{\prime}$, we deduce that $k \in J'_{3x}$ we can  then build  a family of OTs $t_{13x}^{x\in X}$ with the same transition, up to renaming, as the one used to build $t_{12}$ (i.e., $t_1^1$), where ${s^2_{1}}^\prime$ is the same as ${s^1_{1}}^\prime$ up to renaming.
 \[

### 2023-06-26 2021-Refinement/paper/refinementarticleV2.tex
small improvements

@@
 
-Before reasoning on the properties of simulation. we need to introduce one additional notion that characterises when the composition of two automata does not introduce new blocked transitions.
+Before reasoning on the properties of simulation, we need to introduce one additional notion that characterises when the composition of two automata does not introduce new blocked transitions.
 

### 2023-06-27 2021-Refinement/paper/refinementarticleV2.tex
minor

@@
 \]
-If there is a hole equal simulation from $A_1$ to $A_2$, then we say that  $A_2$ simulates $A_1$; we  denote it $A_2\leq A_1$
+If there is a hole-equal simulation from $A_1$ to $A_2$, then we say that  $A_2$ simulates $A_1$; we  denote it $A_2\leq A_1$.
 \end{definition}
@@
 The automaton of \texttt{prod-cons[producer/P]} is shown in Fig.~\ref{Fig:ComposeOA}.
-While the automaton resulting  from the composition of  \texttt{simprod-cons} and \texttt{producer} is bigger and not shown here.
+The automaton resulting  from the composition of  \texttt{simprod-cons} and \texttt{producer} is bigger and not shown here.
 \qed

### 2023-08-30 2021-Refinement/paper/SEFM-Extend-RR.tex
element version rapport de recherche

--- 2023-06-27 2021-Refinement/paper/refinementarticleV2.tex
@@
- \documentclass[runningheads]{llncs}
-
-% TODO: would you like some consistency work in the notations of transitions (esp. True formula and empty map)
-
+%%
+%% This is file `squelette-rr.tex',
+%% generated with the docstrip utility.
+%%
+%% The original source files were:
+%%
+%% RR.dtx  (with options: `sample')
+%% ********************************************************************
+%% Copyright (C) 1997-1999 2004 2006-2011 INRIA/APICS/MARELLE by Jose' Grimm
+%% This file may be distributed and/or modified under the
+%% conditions of the LaTeX Project Public License, either version 1.3
+%% of this license or (at your option) any later version.
+%% The latest version of this license is in
+%%    http://www.latex-project.org/lppl.txt
+%% and version 1.3 or later is part of all distributions of LaTeX
+%% version 2003/12/01 or later.
+%% An archive of the software can be found at
+%%    ftp://ftp-sop.inria.fr/marelle/RR-INRIA
+
+\documentclass[twoside]{article}
+\usepackage[a4paper]{geometry}
+%\usepackage[latin1]{inputenc} % ou 
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc} % ou \usepackage[OT1]{fontenc}
+\usepackage{RR}
 \usepackage{tikz,mathpartir}
 \usepackage{mathtools}
-\usepackage{amsmath,amssymb,mathabx}
+\usepackage{amssymb,mathabx}
+\usepackage{amsthm}
 %\usepackage{unicode-math}
@@
 
+%\newcommand{\qedsymb}{$\blacksquare$}
+
 %\newcommand{\symb}[1]{\makebox{\it #1}}
 \input{common.tex}
-\input{preamble.tex}
+\input{preamble1.tex}
 \input{tikzmacros.tex}
-%\input{macrospNets.sty}
-
-\begin{document}
-%
-\title{Refinements for Open Automata}
-
-%
-%\titlerunning{Abbreviated paper title}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
-\author{
-Rabéa Ameur-Boulifa\inst{1}\orcidID{0000-0002-2471-8012} \and
-Quentin Corradi\inst{2}\orcidID{0000-0003-4218-3987} \and
-Ludovic Henrio \inst{2}\orcidID{0000-0001-7137-3523} \and
-Eric Madelaine \inst{3}\orcidID{0000-0002-5552-5993}}
-%
-\authorrunning{Rab\'ea Ameur-Boulifa et al.}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
-\institute{LTCI, T\'el\'ecom Paris, Institut Polytechnique de Paris, France
-\email{first.last@telecom-paris.fr}\\
+
+%%\usepackage[frenchb]{babel} % optionnel
+\RRNo{7003}
+%% \RTNo{0703}
+%%
+%% date de publication du rapport
+\RRdate{August 2023}
+%%
+%% Cas d'une version deux
+%% \RRversion{2}
+%% date de publication de la version 2
+%% \RRdater{November 2008}
+%%
+\RRauthor{% les auteurs
+ % Premier auteur, avec une note
+Rab\'ea Ameur-Boulifa \thanks{LTCI, T\'el\'ecom Paris, Institut Polytechnique de Paris}%
+  % note partag\'ee (optionnelle)
+ % \and entre chaque auteur s'il y en a plusieurs
   \and
-Universit\'e Lyon, EnsL, UCBL, CNRS, Inria,  LIP, France\\
-\email{first.last@ens-lyon.fr}
- \and
-INRIA Sophia Antipolis M\'edit\'erann\'ee, UCA,  France\\
-\email{first.last@inria.fr}}
-%
-\maketitle              % typeset the header of the contribution
-%
-\begin{abstract}
-%\TODO{ The abstract should briefly summarize the contents of the paper in 150--250 words.}
-
+Quentin Corradi \thanks[sfn]{Universit\'e Lyon, EnsL, UCBL, CNRS, Inria,  LIP}%
+ % r\'ef\'erence \`a la note partag\'ee
+ % liste longue pour tests de mise en page
+\and Ludovic Henrio \thanksref{sfn}   \and Eric Madelaine \thanks{INRIA Sophia Antipolis M\'edit\'erann\'ee, UCA}}
+%% Ceci apparait sur chaque page paire.
+\authorhead{Rab\'ea Ameur-Boulifa et al.}
+%% titre francais long
+\RRtitle{Raffinements des Automates Ouverts\\}
+%% English title
+\RRetitle{Refinements for Open Automata\\ (Extended Version)}
+%%
+\titlehead{Refinements of Open Automata}
+%%
+%\RRnote{This is a note}
+%\RRnote{This is a second note}
+%%
+\RRresume{
+Vérifier la correction d'un programme est une tâche complexe souvent réalisée de manière progressive en établissant une relation entre les comportements de deux programmes.
+Le relation de simulation, qui met en corespondance   une spécification et une implémentation, ou un programme et sa version raffinée, permet d'assurer la correction.
+Cet article introduit et discute d'une relation entre des programmes représentés sous la forme d'\emph{automates ouverts}, un modèle comportemental symbolique pour les systèmes de communication.
+Établir des relations d'équivalence et de raffinement sur les automates ouverts permet une approche compositionnelle pour vérifier leur comportement.
+L'aspect compositionnel des automates ouverts provient des \emph{trous}, qui représentent des éléments du contexte.
+La composition de deux automates consiste à instancier un trou d'un automate avec l'autre automate.
+Dans cet article, nous définissons une relation de raffinement entre les automates ouverts qui peuvent avoir ou non les mêmes trous, sur le modèle des simulations.
+Nous montrons ensuite dans quelles conditions la composition d'automates ouverts préserve cette relation.
+
+}
+\RRabstract{
 Establishing equivalence and refinement relations between programs is an important mean for 
 verifying their correctness. By establishing that the
-behaviours of a modified program simulate those of the source one, simulation relations formalise the desired relation between a specification and an implementation, 
- two equivalent implementations, or a program and its optimised implementation.
-This article discusses a notion of simulation between \emph{open automata}, which are symbolic
-behavioural models for communicating systems. 
+behaviours of a modified program simulate those of the source one, simulation relations formalise the desired relationship between a specification and an implementation,  two equivalent implementations, or a program and its optimised implementation.
+This article discusses a notion of simulation between \emph{open automata}, which are symbolic behavioural models for communicating systems. 
 Open automata may have \emph{holes} modelling elements of their
-context, and can be composed by instantiation of the holes. This allows for a compositional approach for
-verification of their behaviour.
-
+context, and can be composed by instantiation of the holes.
+This allows for a compositional approach for verification of their behaviour.
 We define a simulation between open automata that may or may not have the same holes, and
 show under which conditions these refinements are preserved by composition of open automata.
-
-\keywords{Labelled transition systems   \and Simulation \and Refinement \and Composition.}
-\end{abstract}
+ }
+%%
+\RRmotcle{Syst\`emes de transitions \'etiquet\'ees, Simulation, Raffinement, Composition}
+\RRkeyword{
+Labelled transition systems, Simulation, Refinement, Composition}
+%%
+%% \RRprojet{Apics}  % cas d'un seul projet
+\RRprojets{LTCI and LIP and KAIROS}
+%%
+%% \URLorraine % pour ceux qui sont \`a l'est
+%% \URRennes  % pour ceux qui sont \`a l'ouest
+%% \URRhoneAlpes % pour ceux qui sont dans les montagnes
+%% \URRocq % pour ceux qui sont au centre de la France
+%% \URFuturs % pour ceux qui sont dans le virtuel
+%% \URSophia % pour ceux qui sont au Sud.
+%%
+%% \RCBordeaux % centre de recherche Bordeaux - Sud Ouest
+%% \RCLille % centre de recherche Lille Nord Europe
+%% \RCParis % Paris Rocquencourt
+%% \RCSaclay % Saclay \^Ile de France
+%% \RCGrenoble % Grenoble - Rh\^one-Alpes
+%% \RCNancy % Nancy - Grand Est
+%% \RCRennes % Rennes - Bretagne Atlantique
+\RCSophia % Sophia Antipolis M\'editerran\'ee
+
+%%
+\begin{document}
+%%
+
+\makeRR   % cas d'un rapport de recherche
+%% \makeRT % cas d'un rapport technique.
+%% a partir d'ici, chacun fait comme il le souhaite
+
 %
@@
 The refined model features all the specified behaviours with more concrete details.
-From a formal point of view,  refinement is a mathematical relations between a specification and its implementation, one frequently used relation is trace inclusion or simulation  \cite{Milner:1980,Kouchnarenko:2007}.
+From a formal point of view,  refinement is a mathematical relations between a specification and its implementation, with trace inclusion or simulation being frequently used relations  \cite{Milner:1980,Kouchnarenko:2007}.
 
@@
  of the main automaton has been provided.
-Because of their the generic nature, the notion of OA model is quite abstract but we already illustrated previously how to derive OAs for process algebra operators~\cite{henrio:01299562} or for component systems~\cite{AMHEEMA:2023,ameurboulifa:01526055}.
+Due to their the generic nature, the notion of OA model is quite abstract but we already illustrated previously how to derive OAs for process algebra operators~\cite{henrio:01299562} or for component systems~\cite{AMHEEMA:2023,ameurboulifa:01526055}.
 
 In previous works \cite{AMHEEMA:2023,wang:03126313} a bisimulation relation was defined for OA and open parameterised hierarchical LTSs.
-It has already good properties relatively to bisimulation, but refinement relations were not studied.
+It exhibited good properties concerning bisimulation, but refinement relations were not studied.
 In this article we go further to  define a theory of simulation for OA.
 The simulation relation we introduce in the paper  is based on the notion of   simulation,  in a similar way to that defined in classical automata theory \cite{Milner:1989,Bellegarde:2000}.
-And with the common behaviour-preserving  property:  all the behaviour of the abstract specification must be followed by its (complex) implementation but additional behaviours may exist.
-However we also ensure that a whole scenario, made of several steps, of the specification can also be simulated by the refined system, which is slightly richer than the traditional simulation relation and which allows us to obtain a compositionality result.
+It possesses the common behaviour-preserving  property:  all the behaviour of the abstract specification must be followed by its (complex) implementation but additional behaviours may exist.
+However we also ensure that a whole scenario, made of several steps, of the specification can also be simulated by the refined system, which is slightly richer than the traditional simulation relation and  allows us to obtain a compositionality result.
 
 %This article first introduces OA that were defined in  \cite{henrio:01299562}. %,  but compared to previous works, we and additionally defines the composition of OA.
-Our contribution in this paper is the definition a simulation relation for OA that has the following characteristics:
+Our contribution in this paper is the definition of a simulation relation for OA that has the following characteristics:
 \begin{compactitem}
@@
 Second we introduce a relation that relates two automata with different sets of holes, which allows us to take into account the open nature of OA, and to deal with composition.
-Properties of the simulation are stated and proven on the second, more general version of the relation, they are thus also valid for the first simpler simulation relation.
+Properties of the simulation are stated and proven on the second, more general version of the relation,   thus also being valid  for the first simpler simulation relation.
 
@@
 We  then  define a simulation relation for OA, first only considering two automata with the same set of holes in Section~\ref{sec:refinement} and generalize it to automata with a different set of holes in Section~\ref{sec:holes}.
-Section~\ref{sec:prop} is dedicated to formalize and prove basic properties of the simulation defined; here we prove that simulation is a preorder and has nice composability properties.
+Section~\ref{sec:prop} is dedicated to formalize and prove basic properties of the simulation defined, including the proof that simulation is a preorder and has nice composability properties.
 In Section~\ref{sec:sota} we review related works, and Section~\ref{sec:ccl} concludes the paper.
@@
 %The substitution in \(e \in E\) of \(x \in \fvars{e}\) by \(t \in \terms\), is denoted \(e\subst{t}{x}\), and its generalisation to t
-The parallel substitution of variables in \(V\) by a map \(\psi: V \to \terms\) is denoted \(e\psubst{\psi}\).
+The parallel substitution of variables in \(e\) by a map \(\psi: V \to \terms\) is denoted \(e\psubst{\psi}\).
 
@@
 \end{definition}
+
 A pair consisting of a state and a valuation is called a \emph{configuration} (of the automaton).
@@
 We additionally use arrays of messages with a syntax of the form $\texttt{M[l]}$ for array accesses; $\texttt{M}$ is an array of $\texttt{N}$ elements, from $0$ to $\texttt{N}-1$.
-Finally we use addition and modulo operation ($\%$) on integers.
+Finally, we use addition and modulo operation ($\%$) on integers.
+$\qed$
 
@@
 \end{figure}
-\qed
+
 \end{example}
@@
 Transitions involving \texttt{Q} remain unchanged.
-\qed
+$\qed$
 
@@
 Indeed, one can see that  $\mathcal{R}=\{(r_0,s_0) \mapsto \texttt{l}=\texttt{f}, (r_0,s_1) \mapsto \texttt{f}=\texttt{l}+1\% \texttt{N} \}$ is  a  simulation 
-relation. It follows that  \texttt{prod-cons} $\leq$ \texttt{simprod-cons}. \qed
+relation. It follows that  \texttt{prod-cons} $\leq$ \texttt{simprod-cons}. $\qed$
 \end{example}
@@
 Unfortunately, considering all the common holes does not ensure transitivity of the simulation for the following reason.
-If $A_1$ simulates $A_2$ and $A_2$ simulates $A_3$, and one hole $j$ appears in $A_3$ and in $A_1$ but not in $A_2$ then we have no guarantee on the way $A_1$ and $A_3$ take the actions of this his hole into account, thus  a simulation between and $A_1$ and $A_3$ would require conditions involving actions of the hole $j$ which cannot be ensured.
+If $A_1$ simulates $A_2$ and $A_2$ simulates $A_3$, and one hole $j$ appears in $A_3$ and in $A_1$ but not in $A_2$ then we have no guarantee on the way $A_1$ and $A_3$ take the actions of this  hole into account, thus  a simulation between and $A_1$ and $A_3$ would require conditions involving actions of the hole $j$ which cannot be ensured.
 The way we solve this issue is to remember in the simulation relation which holes have been compared.
@@
 \begin{example}  Consider again the \texttt{prod-cons} and \texttt{simprod-cons}  automata given in the examples above.
-Since  \texttt{prod-cons} $\leq_{\{\texttt{P,Q}\}}$ \texttt{simprod-cons},  then according to Theorem \ref{thm:ContextRefinement},
-\texttt{prod-cons[producer/P]} $\leq_{\{\texttt{Q}\}}$  \texttt{simprod-cons[producer/P]}. 
+Since  \texttt{prod-cons} $\leq_{\{\texttt{P,Q}\}}$ \texttt{simprod-cons},  then according to Theorem \ref{thm:ContextRefinement}, we have
+\texttt{prod-cons[producer/P]} $\leq_{\{\texttt{Q}\}}$  \texttt{simprod-cons[producer/P]}. \\
 The automaton of \texttt{prod-cons[producer/P]} is shown in Fig.~\ref{Fig:ComposeOA}.
 The automaton resulting  from the composition of  \texttt{simprod-cons} and \texttt{producer} is bigger and not shown here.
-\qed
 \end{example}
@@
 If $\wrel{A_1}{A_2}{H}$ then there is $\mathcal{R}_{12}$ a relation between states
-of $A_1$ and of $A_2$;  If $\wrel{A_2}{A_3}{H'}$ then there is $ˇ_{23}$ a relation between states of $A_2$ and of $A_3$. We build a relation between
+of $A_1$ and of $A_2$;  If $\wrel{A_2}{A_3}{H'}$ then there is $\mathcal{R}_{23}$ a relation between states of $A_2$ and of $A_3$. We build a relation between
  states of $A_1$ and of $A_3$ as follows:  for each pair of states $s_1$, $s_3$, for each state $s_2$ such that $\mathcal{R}_{12}$ relates $s_1$ and $s_2$, and $\mathcal{R}_{23}$ relates $s_2$ and $s_3$.
@@
 \end{multline*}
-\qed
+$\qed$
 \end{enumerate}
@@
 \end{multline*}
-which gives the expected result. \qed
+which gives the expected result. $\qed$
 \end{enumerate}
@@
 \end{multline*}
-\qed
+$\qed$
 
@@
 \end{document}
+\endinput
+%%
+%% End of file `squelette-rr.tex'.

### 2023-08-30 2021-Refinement/paper/SEFM-Extend-RR.tex
coorection typo

@@
 %% titre francais long
-\RRtitle{Raffinements des Automates Ouverts\\}
+\RRtitle{Raffinements des Automates Ouverts}
 %% English title
@@
 Vérifier la correction d'un programme est une tâche complexe souvent réalisée de manière progressive en établissant une relation entre les comportements de deux programmes.
-Le relation de simulation, qui met en corespondance   une spécification et une implémentation, ou un programme et sa version raffinée, permet d'assurer la correction.
+La relation de simulation, qui met en corespondance   une spécification et une implémentation, ou un programme et sa version raffinée, permet d'assurer la correction.
 Cet article introduit et discute d'une relation entre des programmes représentés sous la forme d'\emph{automates ouverts}, un modèle comportemental symbolique pour les systèmes de communication.

### 2023-09-01 2021-Refinement/paper/refinementarticleV2.tex
cont. corrections + integration rapport

@@
 verifying their correctness. By establishing that the
-behaviours of a modified program simulate those of the source one, simulation relations formalise the desired relation between a specification and an implementation, 
+behaviours of a modified program simulate those of the source one, simulation relations formalise the desired relationship between a specification and an implementation, 
  two equivalent implementations, or a program and its optimised implementation.
@@
 We informally explain here the symbolic nature of the bisimulation for OA and the related complexity of its definition.
+\RAB{The notion of symbolic bisimulation, as it was introduced in \cite{HENNESSY:1995}, is aimed at computing bisimulation of value-passing processes.
+The class of processes manipulating and exchanging with the environment data, where the values are from possibly infinite domain.}
  The presence of holes in fact raises no strong difficulty but the variables must be handled carefully.
@@
 \begin{definition}[Hole-equal simulation]\label{def:HoleEqualSim}
-Consider two OA with identical set of holes:  \(A_1=\OAg[1]\) and \(A_2=\OAg[2]\) where  \(J_1 = J_2\), the relation on configurations \(\mathcal{R}: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $A_1$ to $A_2$ if the following conditions hold :
+Consider two OA with identical set of holes:
+\(A_1 = \OA{S_1}{s_{01}}{V_1}{\sigma_{01}}{J}{T_1}\) and \(A_2 = \OA{S_2}{s_{02}}{V_2}{\sigma_{02}}{J}{T_2}\), the relation on configurations \(\mathcal{R}: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $A_1$ to $A_2$ if the following conditions hold :
 \item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash \mathcal{R}\mpar{s_{01}, s_{02}}\)
@@
          {
-           \beta_{1 j}^{j\in J}, g_1,\psi_1}
+           \beta_{1 j}^{j\in J'_{1}}, g_1,\psi_1}
          {s_1 \OTarrow {\alpha_1} s_1'} \in \fOT{s_1} .\,~~
@@
          {
-           \beta_{2 x j}^{j\in J}, g_{2 x},\psi_{2 x}}
+           \beta_{2 x j}^{j\in J'_{2x}}, g_{2 x},\psi_{2 x}}
          {s_2 \OTarrow {\alpha_{2 x}} s_{2 x}'}
@@
 
-We now  state the properties of our simulation, their proofs  can be found in the appendices.
+We now  state the properties of our simulation, their formal proofs  can be found in  the extended version of this paper \cite{henrio:hal-04193421}.
 We express these properties  in terms of hole-tracking simulation because, thanks to Property~\ref{lem-sim-sim}   all the properties  of hole-tracking simulation are also valid  for hole-equal simulation.
@@
 % ANS: was copy paste from the report, polished now
+
 The relation  \(\wrel{}{}{H}\) is reflexive,  \(\wrel{A}{A}{H}\).
@@
 %\end{theorem}
-Appendix~\ref{sec:proof-transitivity} presents the proof of transitivity.
+In \cite{henrio:hal-04193421}, we give proof of transitivity.
 It is done classically by identifying the relation between $A_1$ and $A_3$ that is a simulation.
@@
 
-\newpage
-
-\appendix
-
-\section{Proof of Transitivity for Refinement (Theorem~\ref{thm:preoder})}\label{sec:proof-transitivity}
-\begin{quote}
-If $\wrel{A_1}{A_2}{H}$ and $\wrel{A_2}{A_3}{H'}$, then $\wrel{A_1}{A_3}{H\cap H'}$.
-\end{quote}
-
-\proof 
-If $\wrel{A_1}{A_2}{H}$ then there is $\mathcal{R}_{12}$ a relation between states
-of $A_1$ and of $A_2$;  If $\wrel{A_2}{A_3}{H'}$ then there is $ˇ_{23}$ a relation between states of $A_2$ and of $A_3$. We build a relation between
- states of $A_1$ and of $A_3$ as follows:  for each pair of states $s_1$, $s_3$, for each state $s_2$ such that $\mathcal{R}_{12}$ relates $s_1$ and $s_2$, and $\mathcal{R}_{23}$ relates $s_2$ and $s_3$.
-Let $\mathcal{R}_{13}$ be the relation:\\
-  \[\mathcal{R}_{13}(s_1,s_3)=\bigvee_{s_2\in S_2}\mpar{\mathcal{R}_{12}(s_1,s_2) \land \mathcal{R}_{23}(s_2,s_3) } \]
-
-We will show that $\wrel{A_1}{A_3}{H\cap H'}$ by exhibiting  $\mathcal{R}_{13}$ as a hole-tracking simulation of $A_1$ by  $A_3$.
-
-We have to prove that the relation $\mathcal{R}_{13}$ satisfies the three conditions of the definition of a refinement of OA.
-\begin{enumerate}
-\item Firstly, we have to $\mathcal{R}_{13}$ satisfies initial configurations:
-\[\sigma_{01} \uplus \sigma_{03} \vdash \mathcal{R}_{13} \mpar{s_{01}, s_{03}}\]
-By knowing that substitutions only have an effect on the variables of the OA they belong to, they also produce terms containing only variables of the OA they belong to. We have:
-\begin{align*}
-\mpar{\sigma_{01} \uplus \sigma_{02} \vdash \mathcal{R}_{12}\mpar{s_{01}, s_{02}}} \wedge \mpar
-{\sigma_{02} \uplus \sigma_{03} \vdash \mathcal{R}_{23}\mpar{s_{02}, s_{03}}}&\implies\\
-\mathcal{R}_{12}\mpar{s_{01},s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02}} \wedge \mathcal{R}_{23}\mpar{s_{02}, s_{03}}\psubst{\sigma_{02} \uplus \sigma_{03}}&\implies\\
-\mathcal{R}_{12}\mpar{s_{01},s_{02}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} \wedge \mathcal{R}_{23}\mpar{s_{02}, s_{03}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}}&\implies\\
-\underbrace{\mathcal{R}_{12}\mpar{s_{01},s_{02}}\wedge \mathcal{R}_{23}\mpar{s_{02}, s_{03}}}_{\implies \mathcal{R}_{13} \mpar{s_{01}, s_{03}}}\psubst{\sigma_{01} \uplus \sigma_{02} \uplus \sigma_{03}} %&\implies\\
- \end{align*}
-Since $\sigma_{02}$ has no effect on variables of $s_{01}$ and $s_{03}$ thus we get the expected result.
-
-\item 
- Secondly, we need to prove that for any open transition $t_1$ in $T_1$  originating from $s_1$:
-\begin{align*}
-\OTx{1}{}{1}{1} \in \fOT{s_1}
-\end{align*}
-there exists an indexed family of OTs originating from $s_{3}$: 
-\begin{multline*}
-V_1 \uplus  V_3 \uplus \fvars{t_1}
-\vdash\\\hspace{2em}
-\mpar{R_{13}\mpar{s_1, s_3} \wedge g_1 \implies 
-\operatorname*{\bigsymb{\bigvee}}_{z \in Z}
-\mpar{\everymath{\displaystyle}
-\begin{array}{l}
-\alpha_1=\alpha_{3z}\wedge \bigwedge_\subbox{j \in J'_{3z} \cap (H\cap H')} \beta_{1j}=\beta_{3jz} \wedge \\g_{3z}\wedge 
-{R_{12}\mpar{s'_1,s'_{3z}}}\psubst{\psi_1  \uplus \psi_{3z}}
-\end{array}}}
-\end{multline*}	
-The proof of this simulation step follows the same principles as the one given in \cite{AMHEEMA:2023} for the proof of transitivity of bisimulation\footnote{In particular, the bisimulation relation exhibited for proving transitivity is the same.}.
-It relies on  the fact that one open transition of $A_1$ is simulated by a
-family of open transitions of $A_2$, and one open transition of $A_2$ is simulated by a family of open transitions of $A_3$.
-Transitivity leads to a doubly indexed family of simulating open transition.
-
-\item Lastly, we have to prove the satisfaction of the deadlock reduction condition. 
- To build $\mathcal{R}_{13}$ we need to rely on the disjunction of all possible paths to relate $s_1$ and $s_3$, which leads to \[{\displaystyle \mathcal{R}_{13}(s_1,s_3)=\bigvee_{{p\in P}}\mpar{\mathcal{R}_{12}\mpar{s_1,s_{2p}} \wedge \mathcal{R}_{23}\mpar{s_{2p},s_3}}}\]
-
-Consider any $\mpar{s_{1}, s_{3}} \in \mathcal{R}_{13}$  there is a set of states $(s_{2p})^{p\in P}$ of $A_2$ relating  $s_{1}$ and $s_{3}$.
-
-First, according to the relation between $A_1$ and $A_2$ OA,  for all $\mpar{s_1, s_{2p}} \in S_1\times S_2$  we have:
-\begin{multline*}
-%\forall \mpar{s_1, s_{2p}} \in S_1 \times S_2, 
-V_1 \uplus V_2  \vdash \mathcal{R}_{12}\mpar{s_1, s_{2p}} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}  \lor¢ \lnot( \bigvee_\subbox{t_{2p} \in \fOT{s_{2p}}} \fguard{t_{2p}}  )
-\end{multline*}
-Second, according to the relation between $A_2$ and $A_3$ OA, for all $\mpar{s_{2p},s_3} \in S_2\times S_3$  we have:
-\begin{multline*}
- V_2 \uplus V_3  \vdash \mathcal{R}_{23}\mpar{s_{2p},s_3} \implies  \bigvee_\subbox{t_1 \in \fOT{s_{2p}}} \fguard{t_{2p}}  \lor¢ \lnot( \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} )
-\end{multline*}
-With the conjunction of both, we get:
-
-\begin{multline*}
- V_1 \uplus V_2 \uplus V_3  \vdash  \mathcal{R}_{12}\mpar{s_1, s_{2p}} \wedge \mathcal{R}_{23}\mpar{s_{2p},s_3} \implies \\
-  \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} 
- \lor¢ \lnot( \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} )
-\end{multline*}
-
-This is valid for all $s_{2p} \in (s_{2p})^{p\in P}$, then we have:
-\begin{multline*}
- V_1 \uplus V_2 \uplus V_3  \vdash \underbrace{\bigvee_{{p\in P}}\mpar{R_{12}\mpar{s_1, s_{2p}} \wedge R_{23}\mpar{s_{2p},s_3}}}_{R_{13}(s_1,s_3)} \implies \\ ( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )
- \lor¢ \lnot( \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} )
-\end{multline*}
-By removing the $A_2$ variables that have not effect on $A_2$ et $A_3$,
-we get the desired result:
-\begin{multline*}
- V_1 \uplus  V_3  \vdash \mathcal{R}_{13}(s_1,s_3) \implies  ( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )
- \lor¢ \lnot( \bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3} )
-\end{multline*}
-\qed
-\end{enumerate}
-\section{Proof of Context Refinement (Theorem~\ref{thm:ContextRefinement})}
-
-\begin{quote}
-Suppose that $\wrel{A_1}{A_2}{H}$, \(k \in H\) and that \(A_1\subst{A_3}{k}\) is non-blocking. We have: 
-\[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{J_3 \uplus H \setminus \mbrc{k}}\]
-\end{quote}
-\smallskip
-Pictorially, the theorem states the following result:
-
-\begin{center}
-\includegraphics[scale=0.7]{Figures/Thm2intuition}
-\end{center}
-
-\proof
-Let us denote by $A_{13}$ (resp.
-$A_{23}$) the OA resulting from $A_1\subst{A_3}{k}$ (resp.
-$A_2\subst{A_3}{k}$),  to prove the theorem it is sufficient to prove that there exists a relation between states of the two OA that satisfies the conditions of  Definition~\ref{Def:OA-Refinement}.
-
-We denote $A_1=  \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}$ and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and $A_3 = \OA{S_3}{s_{03}}{J_3}{V_3}{\sigma_{03}}{T_3}$.
-The proof requires  to rename the variables of one instance of the two $A_3$ automata to avoid clashes in variable names (this is required by the definition of refinement).
-In practice we will use superscripts ${}^1$ and ${}^2$ to distinguish elements of the two instances of $A_3$.
-
-Let $\mathcal{R}$ be the refinement relation relating states of $A_1$ and $A_2$. 
-Let us denote with $t^1$ and $t^2$  the elements of $A_1$ and $A_2$ respectively.
-Consider any two states $s_{13} = \mpar{s_1,s^1_3}$ and $s_{23} = \mpar{s_2,s^2_3}$ ($s^1_3$ and $s^2_3$  are the same with renaming).
-We define a relation $\mathcal{R}'$ relating states of $s_{13}$ and $s_{23}$ as follows:
-\[ \mathcal{R}' \mpar{s_{13}, s_{23}} = \mathcal{R}\mpar{s_{1}, s_{2}} \land \reach{A_{13}}(s_{13})  %\wedge \reach{A_{13}}\mpar{s_{13}}
- \wedge \bigwedge_\subbox{v_3\in V_3}
- v^1_3=v^2_3\land s^1_3 = s^2_3\]
-
-%\TODO{[Ludo] I believe reachability is not useful here -- to check}
-
-We want to prove that $\mpar{\mathcal{R}', H\uplus J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$. In the following we denote $H'=H\cup J_3 \setminus\{k\}$.
-\begin{enumerate}
-\item First, we have to prove the relation for initial states:
-\[\sigma_{013} \uplus \sigma_{023} \vdash \mathcal{R}'\mpar{s_{013}, s_{023}}\]
-with $\sigma_{013} = \sigma_{01} \uplus \sigma_{03}^1$, $\sigma_{023} = \sigma_{02} \uplus \sigma_{03}^2$, $s_{013}=(s_{01},s_{03}^1)$, and $s_{023}=(s_{02},s_{02}^2)$.\\
-By using the fact that $\mathcal{R}$ relates initial configurations of  $A_1$ and $A_2$, we have:
-$\mpar{\sigma_{01} \uplus \sigma_{02} \vdash \mathcal{R}\mpar{s_{01}, s_{02}}}$.  
-%and based on the  fact that initial states are reachable $\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ we have 
-%\[ \mpar{\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}} \wedge 
-%\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\]
-
-Considering that initial valuations $\sigma_{03}^1$ and $\sigma_{03}^2$ associate the same values to the ``same'' variables modulo renaming, so the following holds:\\ $\left(\,\,{\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }$.
-
-Additionally, because  the domains of the substitution function are disjoint, the substitution function has an effect only on the related elements,  we get:
-\begin{align*}
-& \mpar{\sigma_{01} \uplus \sigma_{02} \vdash \mathcal{R}\mpar{s_{01}, s_{02}}} 
-%\wedge \mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}
-\\
-\implies & \mathcal{R}\mpar{s_{01}, s_{02}}\psubst{ \sigma_{01} \uplus \sigma_{02}}  \land \mpar{\,\,\bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }\\
-\implies & \mpar{\mathcal{R}\mpar{s_{01}, s_{02}} \wedge  \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3 = s^2_3} \psubst{ \sigma_{01} \uplus \sigma_{02} \uplus \sigma^1_{03}\uplus \sigma^2_{03}\uplus \sigma_{013} }\\
-\implies & \sigma_{013} \uplus \sigma_{023} \vdash \mathcal{R}'\mpar{s_{013}, s_{023}}
-\end{align*}
-The last step comes from the additional fact that  $\reach{A_{13}}(s_{013})$.
-
-\item Second, we need to prove for any open transition $t_{13}$ in $T_{13}$ originating from $s_{13}$:
-\begin{align*}
-		&  \OTx{13}{}{13}{13} \in \fOT{s_{13}}
-\end{align*}		
-there exists an indexed family $t_{23x}$ of OTs originating from $s_{23}$ that simulate it: 
-\begin{align*}
-		&  \mpar{\OTx{23}{x}{23x}{23x} \in \fOT{s_{23}}}^{x \in X}
-\end{align*}	
-\begin{align*}		
-		& \text{such that } \mpar{\forall x \in X, J'_{23x} \cap H' = J'_{13} \cap H'} \text{ and }\\
-		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\
-		& \mathcal{R}'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \wedge\\[12pt]
-			 g_{23x} \wedge \mathcal{R}'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
-		\end{array}} 
-	\end{align*}
-
-Recall that by definition of composition and OA refinement we have: 
-\begin{align*}
-&V_{13}= V_1\uplus V^1_3 \text{ and }
-V_{23}= V_2\uplus V^2_3\\
-& H' \subseteq J_3\uplus \mpar{J_1 \cap J_2} \setminus \{k\} = \mpar{J_3\uplus J_1 \setminus \{k\} } \cap \mpar{J_3\uplus J_2 \setminus \{k\}} \\
-\end{align*}
-First of all, we have by hypothesis $\wrel{A_1}{A_2}{H}$, then for any open transition $t_1$ in $T_1$  originating from $s_1$:
-\begin{align*}
-\OTx{1}{}{1}{1} \in \fOT{s_1}
-\end{align*}
-there exists an indexed family of OTs originating from $s_{2}$: 
-\begin{align*}
-\mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_{2}}}^{x \in X} 
-\end{align*}
-such that $\forall x \in X, J'_{2x} \cap H = J'_1 \cap H$ and
-\begin{multline*}
-%\everymath{\displaystyle}
-V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\ \mathcal{R}\mpar{s_1, s_{2}} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj} \nwedge\\
-			 g_{2x} \wedge \mathcal{R}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}}  \qquad \quad (*)
-\end{multline*}	
-\smallskip
-
-Consider any transition $t_{13}$ in $A_{13}$.  Based on  the definition of composition $t_{13}$ can be obtained from two different cases, we will consider the two cases separately.
-
-\paragraph{First case: Both automata perform a transition.}
-The transition $t_{13}$ is obtained by the composition of  transitions $t_1=\OTx{1}{}{1}{1}\in \fOT{s_1}$ and  \[t_3^1=
-\OT{ s^1_3}{{s^1_3}'}{\alpha_3^1}{   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{ g^1_3 }{ \psi^1_3}\in \fOT{s^1_3} \qquad \text{ when } k \in J'_{1} 
-\] The result is:
-\[
-t_{13} = \OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, {s^1_3}'}}{\alpha_1}{\beta_{1j}^{j \in J'_1 \setminus \{k\}} \uplus  {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{g_1 \wedge g^1_3 \wedge \alpha^1_3 = \beta_{1k}}{\psi_1 \uplus \psi^1_3} \qquad \text{ where } k \in J'_{1}
-\]
-We then obtain a family of OTs by the simulation of $A_1$ by $A_2$ (as stated above).
-By hypothesis we have $k \in H$, so in the case where $k \in J'_{1}$, we deduce that $k \in J'_{2x}$ we can  then build  a family of OTs $t_{23x}^{x\in X}$ with the same transitions of $A_3$ (up to renaming) as those used to build $t_{13}$.
-\[
-t_{23x} = \left(\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, {s^2_3}'}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }}{g_{2x} \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2xk}}{\psi_{2x} \uplus \psi^2_3}
-\right)^{x\in X}\]
-Recall that in this case  $k \in J'_{1}$, so $\forall x \in X$ we have
-\begin{align*}
-  J'_{23x} \cap H'  
-&=((J'_{2x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{3} ) \cap (H\uplus J_3 \setminus\{k\} )\\
-&=((J'_{2x}\cap (H\uplus J_3))\uplus (J^{2 \prime}_{3}\cap (H\uplus J_3)))\setminus \mbrc{k}\\
-&=((J'_{2x}\cap H)\uplus (J^{2 \prime}_{3}\cap  J_3))\setminus \mbrc{k}\\
-& \qquad\qquad\qquad\qquad \text{ since } J_3\cap J'_{2x} = \emptyset \text{ and } H\cap J^{2 \prime}_{3} = \emptyset\\
-& =((J'_{2x}\cap H)\uplus J^{2 \prime}_{3})\setminus \mbrc{k}\text{ since } J^{2 \prime}_{3}\subseteq J_3\\
-& =((J'_1\cap H)\uplus J^{1 \prime}_{3})\setminus \mbrc{k}\quad \text{ since } J^{1 \prime}_{3}=J^{2 \prime}_{3} \text{ and } J'_1 \cap H = J'_{2x} \cap H\\
-&= ((J'_1 \cap H) \uplus (J^{1 \prime}_{3} \cap J_3)) \setminus \mbrc{k}\text{ since } J^{1 \prime}_{3}\subseteq J_3\\ 
-& = (J'_1\cap (J_3 \uplus H)) \uplus ((J^{1 \prime}_{3} \cap (J_3 \uplus H)) \setminus \mbrc{k} \\
-& \qquad\qquad\qquad\qquad \text{ since } J_3\cap J'_{1} = \emptyset \text{ and } H\cap J^{1 \prime}_{3} = \emptyset\\
-		& = \mpar{(J'_1  \uplus J^{1 \prime}_{3})\setminus \mbrc{k}} \cap \mpar{(J_{3} \uplus H) \setminus \mbrc{k}}\\
-		& = J'_{13} \cap H'
-\end{align*}
-
-In this case the composition gives: \[g_{13} \Leftrightarrow g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k} \text{ and }
-g_{23x}  \Leftrightarrow g_{2x} \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk}\]
-As $k \in H$ we have   
-$\beta_{1k} = \beta_{2xk}$ then we  deduce:
-\[g^1_3 \wedge \alpha^1_3=\beta_{1k}  \Leftrightarrow g^2_3 \wedge \alpha^2_3= \beta_{2xk}\]
-The proof of the rest  is based on the following facts: 
-\begin{enumerate}
-\item  By construction of  $t_{13}$ and $t_{23x}$ we have $\alpha_{13}=
-\alpha_{1}$ and $\alpha_{23x}=\alpha_{2x}$. So we deduce: 
-$\alpha_{1} = \alpha_{2x} \Rightarrow \alpha_{13} = \alpha_{23x}$.
-\item By composition we have also: \\ $\beta_{13j}^{j\in J'_{13}}= \beta_{1j}^{j \in J'_{1}  \setminus \{k\}} \uplus   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }$
-and $\beta_{23xj}^{j\in J'_{23}}= \beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }$\\
-Therefore, we have for all $j\in J'_{13}$ (recall that $J'_{13}=J'_{23}$):  \[\beta_{13j} = \beta_{23xj} \Rightarrow (j\in J'_1 \land \beta_{1j} = \beta_{2xj}) \vee (j\in J_3^{1\prime} \land \beta^1_{3j}= \beta^2_{3j})\]
-\item 
-Considering $\beta^1_{3j}$ and  $\beta^2_{3j}$  are the same (up to renaming)  we have: \\
-${\displaystyle V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}} \vdash \bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3\implies \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}$\\
-Then we compose by  disjunction with the following hypothesis (part of formula $(*)$).\\ $V_{1} \uplus V_{2} \uplus \fvars{t_1}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}}$
-\begin{align*}
- V_{1} \uplus V_{2}  \uplus V^1_{3} \uplus V^2_{3} \uplus \fvars{t_{13}}\vdash &    \bigwedge_\subbox{v_3\in V_3}\!\!
-v^1_3=v^2_3 \implies {\displaystyle \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}} \vee {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_3} \beta^1_{3j}= \beta^2_{3j}}\\
-\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\!
-v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{2x}   \cap H)\uplus J^{2 \prime}_3 } \beta_{13j} = \beta_{23xj}} \\
-\Rightarrow  V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\!
-v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in    ((J'_{2x}   \cap H)\uplus J^{2 \prime}_3)\setminus \{k\} } \beta_{13j} = \beta_{23xj}} \\
-\Rightarrow    V_{13} \uplus V_{23}  \uplus \fvars{t_{13}}\vdash & \bigwedge_\subbox{v_3\in V_3}\!\!
-v^1_3=v^2_3\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{23x}   \cap H') } \beta_{13j} = \beta_{23xj}}
-\end{align*}
-\end{enumerate}
-
-We can extend the valuation context of the variables to cover the variables of the transitions $t_3$ and the variables in $V_3^1$ and $V_3^2$ in the formula $(*)$.  
-By   using the statements resulting from the cases (a), (b) and (c), we get:
-\begin{multline*}
-V_{13} \uplus V_{23}  \uplus \fvars{t_{13}} \vdash\\
-\mathcal{R}\mpar{s_1, s_{2}} \wedge \mpar{g_1 \wedge g^1_3 \wedge \alpha^1_3=\beta_{1k}}\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3 %\wedge s^1_3=s^2_3
-\implies  \hspace{12em}\\
-\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in (J'_{23x} \cap H')} \beta_{13j}\! =\! \beta_{23xj}\nwedge\\
-			  g_{2x} \wedge \mathcal{R}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}}  \wedge g^2_3 \wedge \alpha^2_3=\beta_{2xk} 
-%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
-\end{multline*}	
-That can be re-written as follows:
-\begin{multline*}
-V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
-\mathcal{R}\mpar{s_1, s_{2}} \wedge g_{13}  \land \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3
-\implies  \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge\\
-			g_{23x} \wedge \mathcal{R}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
-		\end{array}}   
-\end{multline*}
-
-Moreover, we have  for any transition $t_3$ in $A_3$ relating $s_3$ and $s^{\prime}_3$ the following:
-\begin{multline*}
-V_{13} \uplus V_{23}  \uplus \fvars{t_{13}} \vdash\\
-\bigwedge_\subbox{v_3\in V_3}\!\! v^1_3=v^2_3  \wedge s^1_3 = s^2_3 \implies \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3)  \wedge s^{1\prime}_3 = s^{2\prime}_3 
-\end{multline*}
-
- Furthermore,  according to the Definition \ref{Def:Reach} (reachability applied to the composed automaton ${A_1\subst{A_3}{k}}$) we have, for all $t_{13} \in T_{13}$:
-\[ \fvars{t_{13}} \vdash \left(\reach{A_{13}}\mpar{s_{13}} \wedge g_{13} \implies \reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}\right) \]	
-Thus, we get:
-\begin{multline*}
-V_{13} \uplus V_{23} \uplus \fvars{t_1}  \cap \fvars{t_{13}} \vdash\\
-\mathcal{R}\mpar{s_1, s_{2}} \wedge g_{13}  {\wedge \reach{A_{13}}\mpar{s_{13}}}
-\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
-\implies \hspace{5em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge 	g_{23x} \wedge \mathcal{R}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}\\
-		  \wedge {\reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}} 
-\wedge} \bigwedge_\subbox{v_3\in V_3}  \psi_{13}(v^1_3)=\psi_{13}(v^2_3)\wedge s^{1\prime}_3=s^{2\prime}_3
-		\end{array}}   
-\end{multline*}
-
-From the two previous formulas, we get:
-\begin{multline*}
-V_{13} \uplus V_{23} \uplus \fvars{t_{13}}  \vdash\\
-\mathcal{R}\mpar{s_1, s_{2}} \wedge g_{13} \land {\reach{A_{13}}\mpar{s_{13}} \land} \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3 \wedge s^1_3 = s^2_3
-\implies \hspace{7em} \\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge g_{23x}\land  {\reach{A_{13}}\mpar{s_{13}'}\psubst{\psi_{13}}}		\nwedge\\
-			  \mathcal{R}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}} \wedge
- \bigwedge_\subbox{v_3\in V_3}\!\! \psi_{13}(v^1_3)=\psi_{13}(v^2_3) \wedge s^{1\prime}_3 = s^{2\prime}_3
-		\end{array}}   
-\end{multline*}
-
-Because of the independence of the substitution domains, we simplify and get the expected formula:
-	\begin{multline*}
-  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ \mathcal{R}^{\prime}\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge\\[12pt]
-			 g_{23x} \wedge \mathcal{R}^{\prime}\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
-		\end{array}} 
-	\end{multline*}
-
-\smallskip
-
-\paragraph{Second case: Only the encompassing automaton performs a transition.}
- $t_{13}$ is obtained  by  the transition $t_1=\OTx{1}{}{1}{1}$ alone with the state $s^1_3$ unchanged, if $k \not\in J_1'$
-\[t_{13} = \OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, s^1_3}}{\alpha_1}{\beta_{1j}^{j \in J'_1}}{g_1}{\psi_1}
-\]
-As stated above, from the simulation of $A_1$ by $A_2$ we get a  family of OTs $t_{2x}^{x\in X}$. The composition of this family of OTs 
- with the same transitions of $A_3$ (up to renaming) as those used to build $t_{13}$ 
-produces  a family of OTs $t_{23x}^{x\in X}$ in the form:
-\[t_{23x} = \left(
-\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, s^2_3}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x}}}{g_{2x}}{\psi_{2x}} \right)^{x\in X}\]
-
-By hypothesis we have   $k \in H$, since $k \not\in J'_{1}$,  we deduce $k \not\in J'_{2x}$. \\
-$\forall x \in X$ we have:
-\begin{align*}		
-J'_{23x} \cap H' & = J'_{2x}  \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
-& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
-& = \mpar{J'_1\cap H } \text{  since } J'_1 \cap H = J'_{2x} \cap H\\
-& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'
-\end{align*}
-
-The proof of the rest of the formula follows the same steps as the previous case the only argument that change is that by composition we obtain:  $g_{13} $ is the same as $ g_1$ and $g_{23x}$  is the same as $g_{2x}$ and the actions of $\alpha_{13}$, resp.
-$\alpha_{23x}$, is the same as  $\alpha_{1}$, resp.
-$\alpha_{2x}$.
-Similarly $\beta_{13j}$ and $\beta_{23xj}$ that are the same as $\beta_{1j}$ and $\beta_{2xj}$ respectively.
- We also apply the reachability definition but only on the automaton $A_1$
-
-%
-%These two cases define (depending on how $t_{13}$ is built) the family $t_{23x}$ of OTs we are looking for.
-%Thus, for both cases we have to prove the following:
-%\begin{align*}		
-%		&\mpar{\forall x \in X, J'_{23x} \cap H' =
-% J'_{13} \cap H'} \text{ and }\\
-%		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash\\ & R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-%			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \nwedge\\[12pt]
-%			g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
-%		\end{array}} 
-%	\end{align*}
-%	
-%Recall in this second case, i.e. where only $A_1$ performs a transition $t_{13}$,  $k \notin J'_1$, $\forall x \in X$ we have
-%\begin{align*}		
-%J'_{23x} \cap H' & = J'_{2x}  \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
-%& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
-%& = \mpar{J'_1\cap H } \text{  since } J'_1 \cap H = J'_{2x} \cap H\\
-%& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'
-%\end{align*}
-%
-%The proof of the rest of the formula follows the same steps as the previous case the only argument that changes is that by composition we obtain:  $g_{13} \Leftrightarrow g_1$ and
-%$g_{23x}  \Leftrightarrow g_{2x}$.\\
-
-\item Lastly, we have to prove the satisfaction of the deadlock reduction condition, i.e., for all $\mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}$
-\begin{multline*}
-V_{13} \uplus V_{23}  \vdash  \mathcal{R}\mpar{s_{13}, s_{23}} \nwedge  \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}) \implies   \neg (\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
-\end{multline*}
-
-By hypothesis  the composition  \(A_1\subst{A_3}{k}\) is non-blocking,  then according to the Definition \ref{Def:Non-block} we have for all state $s_{13}$:
-
-\begin{multline*}
-V_{13} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1}  \vdash  \left(\reach{A_{13}(s_{13})} \land \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}\right) \implies \bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}
-\end{multline*}
-From this we can infer:
-\begin{multline*}
-V_{13}  \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash  \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})  \implies   \neg(\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}) \lor
-\neg{\reach{A_{13}(s_{13})}}
-\end{multline*}
-
-Furthermore, from the second  hypothesis  stating that $\wrel{A_1}{A_2}{H}$,  we have for all  $\mpar{s_1, s_2} \in S_1 \times S_2$ 
-\begin{multline*}
-V_1 \uplus V_2 \vdash \mathcal{R}\mpar{s_1, s_2} \nwedge \neg (\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}) \implies   \neg(\bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2})
-\end{multline*}
-
-From the two previous formula can deduce:
-\begin{multline*}
-V_{13} \uplus V_2 \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1} \vdash\\ R\mpar{s_1, s_2} \nwedge \neg(\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})  \implies   \neg(\bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2})
-\lor \neg{\reach{A_{13}}(s_{13}) }
-\end{multline*}
-
-By definition of the composition of open automata, each guard of automaton 
- $A_{23}$ is of the form $\fguard{t_{23}} = \fguard{t_{2}}\land t$,  thus we have:
-\begin{multline*}
-V_{23}   \vdash \neg(\bigvee_\subbox{t_1 \in \fOT{s_2}} \fguard{t_2}) \implies \neg(\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}})
-\end{multline*}
-
-From the two previous formula and by introducing the following tautology\\ $ \mpar{\,\,\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}$, we get: 
-\begin{multline*}
-V_{13} \uplus V_{23}  \vdash \!
-\underbrace{\mathcal{R}\mpar{s_1, s_2}\!
-\wedge \!\reach{A_{13}}(s_{13}) \!\land\!
-\mpar{\,\,\bigwedge_\subbox{v_3\in V_3}  v^1_3\!=\!v^2_3 \wedge s^1_3\!=\!s^2_3}}_{\mathcal{R}^{\prime}(s_{13},s_{23})} \wedge \neg\!\!{\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}}   \\ \implies \left(\,\neg{\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}} \lor \neg{\reach{A_{13}}(s_{13}) }\right) \land \reach{A_{13}}(s_{13})
-\implies \neg\!{\bigvee_\subbox{t_{23} \in \fOT{s_{23}}} \fguard{t_{23}}}
-\end{multline*}
-which gives the expected result. \qed
-\end{enumerate}
-
-%\section{a recuperer si on se rend compte que c'est utile}
-%When we will introduce refinements in Section \ref{sec:prelref}, setting an undefined variable will be considered a valid refinement, for instance a \(5\) bits register is a particular \(n\) bits register.
-
-\section{Proof of Congruence (Theorem~\ref{thm:CongurenceRefinement})}
-\begin{quote}
-Suppose $\wrel{A_2}{A_3}{H}$ and  $k \in H$.  and the composition $A_1\subst{A_2}{k}$ is non-blocking. We have: \[\wrel{A_1\subst{A_2}{k}}{A_1\subst{A_3}{k}}{J_1 \uplus H \setminus \mbrc{k}}\]
-\end{quote}
-\smallskip
-Pictorially, the theorem states the following result:
-
-\begin{center}
-\includegraphics[scale=0.7]{Figures/Thm1intuition}
-\end{center}
-\proof
-Let us denote by $A_{12}$ (resp.
-$A_{13}$) the OA resulting from $A_1\subst{A_2}{k}$ (resp.
-$A_1\subst{A_3}{k}$),  to prove the theorem it is sufficient to prove that there exists a relation between states of the two OA that satisfies the conditions of the Definition~\ref{Def:OA-Refinement}.
-
-We denote $A_1=  \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}$ and \(A_2 = \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and $A_3 = \OA{S_3}{s_{03}}{J_3}{V_3}{\sigma_{03}}{T_3}$.
-
-% The proof requires  to rename the variables of one instance of the two $A_3$ automata to avoid clashes in variable names (this is required by the definition of refinement).
-In practice we will use superscripts ${}^1$ and ${}^2$ to distinguish elements of the two instances of $A_3$.
-
-Let $R$ be the refinement relation relating states of $A_2$ and $A_3$. 
-Let us denote with $t^2$ and $t^3$  the elements of $A_2$ and $A_3$ respectively.
-Consider any two states $s_{12} = \mpar{s^1_1,s_2}$ and $s_{13} = \mpar{s^2_1,s_3}$ ($s^1_1$ and $s^2_1$  are the same with renaming).
-We define a relation $\mathcal{R}'$ relating states of $s_{12}$ and $s_{13}$ as follows:
-\[\mathcal{R}' \mpar{s_{12}, s_{13}} = \mathcal{R}\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1}
- v^1_1=v^2_1\wedge s^1_1 = s^2_1\]
-Let us denote $H'=H\cup J_1 \setminus\{k\}$.
-We want to prove that $\mpar{\mathcal{R}', H'}$  is a hole-tracking simulation of $A_{12}$ and $A_{13}$. As for the previous proof we deal with cases:
-\begin{enumerate}
-\item First, we have to prove the relation for initial states:
-\[\sigma_{012} \uplus \sigma_{013} \vdash \mathcal{R}'\mpar{s_{012}, s_{013}}\]
-with $\sigma_{012} = \sigma_{01}^1 \uplus \sigma_{03}$, $\sigma_{013} = \sigma_{01}^2 \uplus \sigma_{03}$, $s_{012}=(s_{01}^1,s_{02})$, and $s_{013}=(s_{01}^2,s_{03})$.\\
-The proof of this point is similar to that of Theorem \ref{thm:ContextRefinement}.
-\item Second, we need to prove for any OT $t_{12}$ in $T_{12}$ originating from $s_{12}$
-
-\begin{align*}
-		&  \OTx{12}{}{12}{12} \in \fOT{s_{12}}
-\end{align*}		
-there exists an indexed family $t_{13x}$ of OTs originating from $s_{13}$ that simulates it: 
-\begin{align*}
-		&  \mpar{\OTx{13}{x}{13x}{13x} \in \fOT{s_{13}}}^{x \in X}
-\end{align*}	
-such that  $\mpar{\forall x \in X, J'_{13x} \cap H' = J'_{12} \cap H'}$ and
-\begin{multline*}	
-V_{12} \uplus V_{13} \uplus \fvars{t_{12}} \vdash\\ \mathcal{R}'\mpar{s_{12}, s_{13}} \wedge g_{12} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
-			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \wedge\\[12pt]
-			 g_{13x} \wedge \mathcal{R}'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
-		\end{array}} 
-	\end{multline*}
-By definition of composition and OA refinement we have: 
-\begin{align*}
-&V_{12}= V^1_1\uplus V_3 \text{ and }
-V_{13}= V^2_1\uplus V_3\\
-& H'=H\uplus J_1 \setminus \{k\} \subseteq J_1\uplus \mpar{J_2 \cap J_3} \setminus \{k\}= \mpar{J^1_1\uplus J_2 \setminus \{k\} } \cap \mpar{J^2_1\uplus J_3 \setminus \{k\}} \\ &\,\,\,\,\, = J_{12 } \cap J_{13}
-\end{align*}
-We have by hypothesis $\wrel{A_2}{A_3}{H}$, then for any open transition $t_2$ in $T_2$  originating from $s_2$:
-\begin{align*}
-\OTx{2}{}{2}{2} \in \fOT{s_2}
-\end{align*}
-there exists an indexed family of OTs originating from $s_{3}$: 
-\begin{align*}
-\mpar{\OTx{3}{x}{3x}{3x} \in \fOT{s_{3}}}^{x \in X} 
-\end{align*}
-such that $\forall x \in X, J'_{3x} \cap H = J'_2 \cap H$ and
-\begin{multline*}
-%\everymath{\displaystyle}
-V_2 \uplus V_3 \uplus \fvars{t_2} \vdash\\ \mathcal{R}\mpar{s_2, s_3} \wedge g_2 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_2 = \alpha_{3x} \wedge \bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj} \nwedge\\
-			 g_{3x} \wedge \mathcal{R}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
-		\end{array}}  \qquad \quad (*)
-\end{multline*}	
-\smallskip
-
-Consider any transition $t_{12}$ in $A_{12}$. Based on the definition of the composition  $t_{12}$ can be obtained from two different cases,  we will consider the two cases
-separately.
-
-\paragraph{First case: Both automata perform a transition.} The transition $t_{12}$  is obtained by the composition of transition $t_2=\OTx{2}{}{2}{2}$ and a transition \[t_1^1=
-\OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{   {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1} \qquad \text{ when } k \in {J^1_{1}}^{\prime}
-\] The result:
-%%%% Attention deactiver ici
-\[
-t_{12} = \OT{\mpar{s^1_1, s_2}}{\mpar{{s^1_1}',s'_2 }}{\alpha^1_1}{{\beta^1_{1j}}^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {(\beta_{2j})^{j \in J^{\prime}_2} }}{g^1_1 \wedge g_2 \wedge \alpha^1_1 = \beta_{2k}}{\psi^1_1 \uplus \psi_2} \qquad \text{ where } k \in {J^1_{1}}^{\prime}
-\]
-
-We then obtain a family of OTs by the simulation of $A_2$ by $A_3$ (as stated above).
-By hypothesis we have $k \in H$, so in the case where $k \in {J^1_{1}}^{\prime}$, we deduce that $k \in J'_{3x}$ we can  then build  a family of OTs $t_{13x}^{x\in X}$ with the same transition, up to renaming, as the one used to build $t_{12}$ (i.e., $t_1^1$), where ${s^2_{1}}^\prime$ is the same as ${s^1_{1}}^\prime$ up to renaming.
-\[
-t_{13x} = \left(\OT{\mpar{s^2_1, s_3}}{\mpar{{s^2_{1}}',s'_{3x}}}{\alpha^2_{1}}  {{(\beta^2_{1j})^{j \in J^{2 \prime}_1}}\uplus \beta_{3xj}^{j \in J'_{3x}  \setminus \{k\}} }{g_{3x} \wedge g^2_1 \wedge \alpha^2_1 = \beta_{3xk}}{\psi_{3x} \uplus \psi^2_1}
-\right)^{x\in X}\]
-Recall that in this case  $k \in {J^1_{1}}^{\prime}$, so $\forall x \in X$ we have:
-\begin{align*}
-  J'_{13x} \cap H'  
-&=((J'_{3x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{1} ) \cap (H\uplus J_1 \setminus\{k\} )\\
-&=((J'_{3x}\cap (H\uplus J_1))\uplus (J^{2 \prime}_{1}\cap (H\uplus J_1)))\setminus \mbrc{k}\\
-&=((J'_{3x}\cap H)\uplus (J^{2 \prime}_{1}\cap  J_1))\setminus \mbrc{k}\\
-& \qquad\qquad\qquad\qquad\text{ since } J_1\cap J'_{3x} = \emptyset \text{ and } H\cap J^{2 \prime}_{1} = \emptyset\\
-& =((J'_{3x}\cap H)\uplus J^{2 \prime}_{1})\setminus \mbrc{k}\text{ since } J^{2 \prime}_{1}\subseteq J_1\\
-& =((J'_2\cap H)\uplus J^{1 \prime}_{1})\setminus \mbrc{k}\\
-& \qquad\qquad\qquad\qquad \text{ since } J^{1 \prime}_{1}=J^{2 \prime}_{1} \text{ and } J'_2 \cap H = J'_{3x} \cap H\\
-&= ((J'_2 \cap H) \uplus (J^{1 \prime}_{1} \cap J_1)) \setminus \mbrc{k}\text{ since } J^{1 \prime}_{1}\subseteq J_1\\ 
-& = (J'_2\cap (J_1 \uplus H)) \uplus ((J^{1 \prime}_{1} \cap (J_1 \uplus H)) \setminus \mbrc{k}\\
-& \qquad\qquad\qquad\qquad \text{ since } J_1\cap J'_{2} = \emptyset \text{ and } H\cap J^{1 \prime}_{1} = \emptyset\\
-		& = \mpar{(J'_2  \uplus J^{1 \prime}_{1})\setminus \mbrc{k}} \cap \mpar{(J_{1} \uplus H) \setminus \mbrc{k}}\\
-		& = J'_{12} \cap H'
-\end{align*}
-
-In this case the composition gives: \[g_{12} \Leftrightarrow g^1_1 \wedge g_2 \wedge \alpha^1_1=\beta_{2k} \text{ and }
-g_{13x}  \Leftrightarrow g^2_1 \wedge g_{3x} \wedge  \alpha^2_1=\beta_{3xk}\]
-As $k \in H$ we have   
-$\alpha^1_1= \alpha^2_1$ then we  deduce:
-\[g^1_1 \wedge \alpha^1_1=\beta_{2k}  \Leftrightarrow g^2_1 \wedge \alpha^2_1= \beta_{3xk}\]
-
-The proof of the rest  is based on the following facts: 
-\begin{enumerate}
-\item     By construction of  $t_{12}$ and $t_{13x}$ we have $\alpha_{12}=
-\alpha^1_{1}$ and $\alpha_{13x}=\alpha^2_{1}$. Since  $\alpha^1_{1}$ and  $\alpha^2_{1}$ are the same (up to renaming) we deduce: 
-$\alpha_{12} = \alpha_{13x}$.
-\item By composition we have also: \\ $\beta_{12j}^{j\in J'_{12}}= (\beta^1_{1j})^{j \in J^{1 \prime}_{1} \setminus \{k\}} \uplus   (\beta_{2j})^{j \in J'_{2} }$
-and $\beta_{13xj}^{j\in J'_{13}}= (\beta^2_{1j})^{j \in J^{2 \prime}_{1}  \setminus \{k\}}  \uplus \beta_{3xj}^{j \in J'_{3x}  \setminus \{k\}}$\\
-Therefore, we have for all $j\in J'_{12}$ (recall that $J'_{12}=J'_{13}$):  \[\beta_{12j} = \beta_{13xj} \Rightarrow (j\in J^{1\prime}_1 \land \beta^1_{1j} = \beta^2_{1j}) \vee (j\in J'_2 \land \beta_{2j}= \beta_{3xj})\]
-\item 
-Considering $\beta^1_{1j}$ and  $\beta^2_{1j}$  are the same (up to renaming)  we have: \\
-${\displaystyle V^1_{1} \uplus V^2_{1} \uplus \fvars{t_{12}} \vdash \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1\implies \bigwedge_\subbox{j \in J^{2 \prime}_1} \beta^1_{1j}= \beta^2_{1j}}$\\
-We compose by disjunction with the following hypothesis (part of formula $(*)$).\\ $V_{2} \uplus V_{3} \uplus \fvars{t_2}  \vdash {\displaystyle \bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj}}$
-\begin{align*}\hspace{-5ex}
- V_{2} \uplus V_{3}  \uplus V^1_{1} \uplus V^2_{1} \uplus \fvars{t_{12}}\vdash &    \bigwedge_\subbox{v_1\in V_1}\!\!
-v^1_1=v^2_1 \implies {\displaystyle \bigwedge_\subbox{j \in J'_{3x} \cap H} \beta_{2j} = \beta_{3xj}} \vee {\displaystyle \bigwedge_\subbox{j \in J^{2 \prime}_1} \beta^1_{1j}= \beta^2_{1j}}\\
-\Rightarrow  V_{12} \uplus V_{13}  \uplus \fvars{t_{12}}\vdash & \bigwedge_\subbox{v_1\in V_1}\!\!
-v^1_1=v^2_1\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{3x}   \cap H)\uplus J^{2 \prime}_1 } \beta_{12j} = \beta_{13xj}} \\
-\Rightarrow  V_{12} \uplus V_{13}  \uplus \fvars{t_{12}}\vdash & \bigwedge_\subbox{v_1\in V_1}\!\!
-v^1_1=v^2_1\implies {\displaystyle \bigwedge_\subbox{j \in    ((J'_{3x}   \cap H)\uplus J^{2 \prime}_1)\setminus \{k\} } \beta_{12j} = \beta_{13xj}} \\
-\Rightarrow    V_{12} \uplus V_{12}  \uplus \fvars{t_{12}}\vdash & \bigwedge_\subbox{v_1\in V_1}\!\!
-v^1_1=v^2_1\implies {\displaystyle \bigwedge_\subbox{j \in (J'_{13x}   \cap H') } \beta_{12j} = \beta_{13xj}}
-\end{align*}
-\end{enumerate}
-
-We can extend the valuation context of the variables to cover the variables of the transitions $t_1$ and variables $V_1^1$ and $V_1^2$ in the formula $(*)$.
-By using the statements resulting from the cases (a), (b) and (c), we get:
-\begin{multline*}
-V_{13} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash\\
-\mathcal{R}\mpar{s_2, s_{3}} \wedge \mpar{g_2 \wedge g^1_1 \wedge \alpha^1_1=\beta_{2k}}\wedge \bigwedge_\subbox{v_1\in V_1}  v^1_1=v^2_1 %\wedge s^1_1=s^2_1
-\implies  \hspace{12em}\\
-\operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in (J'_{13x} \cap H')} \beta_{12j}\! =\! \beta_{13xj}\nwedge\\
-			  g_{3x} \wedge \mathcal{R}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
-		\end{array}}  \wedge g^2_1 \wedge \alpha^2_1=\beta_{3xk} 
-%\wedge \bigwedge_\subbox{v_3\in V_3}  v^1_3=v^2_3\wedge s^1_3=s^2_3
-\end{multline*}	
-That can be re-written as follows:
-\begin{multline*}
-V_{12} \uplus V_{13} \uplus \fvars{t_{12}}  \vdash\\
-\mathcal{R}\mpar{s_2, s_{3}} \wedge g_{12}  \land \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1
-\implies  \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge\\
-			g_{13x} \wedge \mathcal{R}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}}
-		\end{array}}   
-\end{multline*}
-
-Moreover, we have  for any transition $t_1 $ in $A_1$ relating $s^1_1$ and ${s^1_1}^{\prime}$ the following:
-\begin{multline*}
-V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash\\
-\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1  \wedge s^1_1 = s^2_1 \implies \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{13x}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1 
-\end{multline*}
-
-From the two previous formula, we get: 
-\begin{multline*}
-V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash\\
-R\mpar{s_2, s_{3}} \wedge g_{12}  \land \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1  \wedge s^1_1 = s^2_1 
-\implies \hspace{12em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge g_{13x} \wedge \\
-			 R\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}} \wedge \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{13x}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1
-		\end{array}}   
-\end{multline*}
-
- Furthermore, according to the Definition \ref{Def:Reach} (reachability, applied to the composed automaton \(A_1\subst{A_2}{k}\)) we have, for all $t_{12} \in T_{12}$:
-\[ \fvars{t_{12}} \vdash \left(\reach{A_{12}}\mpar{s_{12}} \wedge g_{12} \implies \reach{A_{12}}\mpar{s_{12}'}\psubst{\psi_{12}}\right) \]
-
-Thus, we get:
-\begin{multline*}
-V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash\\
-\mathcal{R}\mpar{s_2, s_{3}} \wedge g_{12} \land \reach{A_{12}}\mpar{s_{12}} \land \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1  \wedge s^1_1 = s^2_1 
-\implies \hspace{12em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge g_{13x} \wedge \\
-			 \mathcal{R}\mpar{s'_2, s'_{3x}}\psubst{\psi_2 \uplus \psi_{3x}} \land \reach{A_{12}}\mpar{s_{12}'}\psubst{\psi_{12}} \\
-\wedge \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{13x}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1
-		\end{array}}   
-\end{multline*}
-
-Because of the independence of the substitution domains, we simplify and get the expected formula:
-\begin{multline*}
-V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash
-\mathcal{R}'\mpar{s_{12}, s_{13}} \wedge g_{12} 
-\implies \hspace{10em}\\ \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}
-\begin{array}{l}
-			\alpha_{12} = \alpha_{13x} \wedge \bigwedge_\subbox{j \in J'_{13x} \cap H'} \beta_{12j} = \beta_{13xj} \nwedge g_{13x} \wedge 
-			 \mathcal{R}'\mpar{s'_{12}, s'_{13x}}\psubst{\psi_{12} \uplus \psi_{13x}}
-		\end{array}}   
-\end{multline*}
-
-\paragraph{Second case: Only the encompassing automaton performs a transition.}
-  $t_{12}$ is obtained by the transition 
-$t^1_1=\OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{{(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1}$  alone with the state $s_2$ unchanged, if $k \not\in {J^1_{1}}^{\prime}$
-\[t_{12} = \OT{\mpar{s^1_1, s_2}}{\mpar{{s^1_1}', s_2}}{\alpha_1^1}{ {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{g^1_1}{\psi^1_1}
-\]
-%As stated above, from the simulation of $A_2$ by $A_3$ we get a  family of OTs $t_{3x}^{x\in X}$. The composition of this family of OTs 
-% with the same transitions of $A_1$ (up to renaming) as those used to build $t_{12}$ 
-%produces  a family of OTs $t_{13x}^{x\in X}$ in the form:
-%\[t_{13x} = \left(\OT{\mpar{s^2_1, s_{3}}}  {\mpar{s^{2\prime}_1, s_{3}}}  {\alpha_1^2}{{(\beta^2_{1j})^{j \in J^{2 \prime}_1} }}{ g^2_1 }{\psi^2_1} \right) \]
-
-%\TODO{NEW -- a refaire en plus joli}
-
-The hole is not involved we can define $t_{13}$ with the same transition $t_1$ of $A_1$ (where elements of $t_1$ are the same as above modulo renaming of variables):
-\[t_{13} = \OT{\mpar{s^1_1, s_3}}{\mpar{{s^2_1}', s_3}}{\alpha_1^2}{ {(\beta^2_{1j})^{j \in {J^{2}_1}'} }}{g^2_1}{\psi^2_1}
-\]
-We thus take $({t_{13 x}})^{x\in X} = \{t_{13}\}$.
-$\forall x \in X$ we have $J'_{13x} =  {J^{2}_1}'$ and trivially:
-\begin{align*}		
-J'_{13x} \cap H' & =  J^{2 \prime}_1 \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \\
-& =  J^{1 \prime}_1 \cap \mpar{J_1 \uplus H \setminus \mbrc{k}} \text{ since }  J^{2 \prime}_1 =  J^{1 \prime}_1\\
-& = \mpar{J'_{12}\cap H' }
-\end{align*}
-
-Moreover, we have by definition 
-\[\mathcal{R}' \mpar{s_{12}, s_{13}} =  \mathcal{R}\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge s^1_1 = s^2_1 \]
-Thus, because transitions $t^1_1$ and  $t^2_1$ are the same:
-\[\mathcal{R}' \mpar{s_{12}, s_{13}} \implies
-\underbrace{\mathcal{R}\mpar{s_{2}, s_{3}} \land \reach{A_{12}}(s_{12}) \wedge \bigwedge_\subbox{v_1\in V_1} v^1_1=v^2_1\wedge {s^1_1}^\prime = {s^2_1}^\prime}_{\mathcal{R}' \mpar{s'_{12}, s'_{13}}}
-\]
-
-Moreover, we have  the following:
-\begin{multline*}
-V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash\\
-\bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1  \wedge s^1_1 = s^2_1 \implies \bigwedge_\subbox{v_1\in V_1}\!\! \psi_{12}(v^1_1)=\psi_{13}(v^2_1)  \wedge s^{1\prime}_1 = s^{2\prime}_1 
-\end{multline*}
-
- Furthermore, according to the Definition \ref{Def:Reach} (reachability, applied to the composed automaton \(A_1\)) we have, for all $t_{12} \in T_{12}$:
-\[ \fvars{t_{12}} \vdash \left(\reach{A_{12}}\mpar{s_{12}} \wedge g_{12} \implies \reach{A_{12}}\mpar{s_{12}'}\psubst{\psi_{12}}\right) \]
-
-Because $\alpha_{12}$ and $\alpha_{13}$ are the same, and also  $\beta_{12}$ and $\beta_{13}$ are the same (modulo renaming of variables), we deduce from the above the expected formula (instantiated with $X$ a singleton): %From the above we can deduce the expected formula:
-\begin{multline*}
-V_{12} \uplus V_{13}  \uplus \fvars{t_{12}} \vdash
-\mathcal{R}'\mpar{s_{12}, s_{13}} \wedge g_{12} 
-\implies \hspace{10em}\\ %\operatorname*{\bigsymb{\bigvee}}_{x \in X}
- \mpar{\everymath{\displaystyle}
-%\begin{array}{l}
-			\alpha_{12} = \alpha_{13} \wedge \bigwedge_\subbox{j \in J'_{13} \cap H'} \beta_{12j} = \beta_{13j} \nwedge g_{13} \wedge 
-			 \mathcal{R}'\mpar{s'_{12}, s'_{13}}\psubst{\psi_{12} \uplus \psi_{13}}
-%		\end{array}
-}   
-\end{multline*}
-
-%By hypothesis we have   $k \in H$ and $k \not\in J^{1\prime}_1$, then $k \not\in J^{2\prime}_1$.
-
-\item Lastly, we have to prove the satisfaction of the deadlock reduction condition, i.e., for all $\mpar{s_{12}, s_{13}} \in S_{12} \times S_{13}$
-\begin{multline*}
-V_{12} \uplus V_{13}  \vdash  \mathcal{R}'\mpar{s_{12}, s_{13}} \nwedge  \neg(\bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}) \implies   \neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})
-\end{multline*}
-
-Let's start  with the hypothesis of the theorem stating that $\wrel{A_2}{A_3}{H}$, thus we have for all  $\mpar{s_2, s_3} \in S_2 \times S_3$ 
-\begin{multline*}
-V_2 \uplus V_3  \vdash\mathcal{R}\mpar{s_2, s_3} \nwedge \neg (\bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}) \implies   \neg(\bigvee_\subbox{t_3 \in \fOT{s_3}} \fguard{t_3})
-\end{multline*}
-
-By hypothesis  the composition  \(A_1\subst{A_2}{k}\) is non-blocking,  then according to the Definition \ref{Def:Non-block} we have for all state $s_{12}$:
-
-\begin{multline*}
-V_{12} \uplus \biguplus_\subbox{t_1 \in \fOT{s_1}} \fvars{t_1}  \vdash  \left(\reach{A_{12}(s_{12})} \land \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}\right) \implies \bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}
-\end{multline*}
-
-Which implies 
-\begin{multline*}
-V_{12} \uplus\! \biguplus_\subbox{t_1 \in \fOT{s_1}}\! \fvars{t_1}  \vdash 
-\neg\!{ \bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}}
-\!\implies\! \!
-\left(\neg{\reach{A_{12}(s_{12})} }\lor \neg\!{\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
-\right)
-\end{multline*}
-
-Additionally, each transition $t_{13}$ of OT$(s_{13})$ is of the form $
-g_1\land g_3 \land g$ with $g_1$ a guard of a transition $t_{1}$ of OT$(s_{1})$.
-Thus we have
-\[
-\neg{\bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}  \implies \neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}}) \]
-
-Thus we have, as $\mathcal{R}$ contains the reachability of state $s_{12}$:
-\begin{multline*}
-V_{12} \uplus V_{13}  \vdash  \mathcal{R}'\mpar{s_{12}, s_{13}} \nwedge  \neg(\bigvee_\subbox{t_{12} \in \fOT{s_{12}}} \fguard{t_{12}}) \implies \\
- \left(\reach{A_{12}(s_{12})} \land \left(\neg{\reach{A_{12}(s_{12})} }\lor
-\neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})\right) 
-\implies
-\neg (\bigvee_\subbox{t_{13} \in \fOT{s_{13}}} \fguard{t_{13}})\right)
-\end{multline*}
-\qed
-
-\end{enumerate}
-
 \end{document}

### 2023-09-01 2021-Refinement/paper/refinementarticleV2.tex
Correct definition 8 and affiliation

@@
 Rabéa Ameur-Boulifa\inst{1}\orcidID{0000-0002-2471-8012} \and
-Quentin Corradi\inst{2}\orcidID{0000-0003-4218-3987} \and
+Quentin Corradi\inst{4}\orcidID{0000-0003-4218-3987} \and
 Ludovic Henrio \inst{2}\orcidID{0000-0001-7137-3523} \and
@@
 \institute{LTCI, T\'el\'ecom Paris, Institut Polytechnique de Paris, France
-\email{first.last@telecom-paris.fr}\\
+\email{first.last@telecom-paris.fr}
 \and
@@
 INRIA Sophia Antipolis M\'edit\'erann\'ee, UCA,  France\\
-\email{first.last@inria.fr}}
+\email{first.last@inria.fr}
+\and
+Imperial College London, United Kingdom (previously Universit\'e Lyon)\\
+\email{qc322[at]ic.ac.uk}}
 %
@@
 %\everymath{\displaystyle}\begin{array}{l}
-V_1 \uplus V_2 \uplus  \fvars{t_1} \uplus \bigcup_x\fvars{t_{2x}}  \vdash \hspace{7cm}
+V_1 \uplus V_2 \uplus  \fvars{t_1} \vdash \bigsymb{\bigexists} \mpar{\bigcup_x\fvars{t_{2x}}}. \hspace{7cm}
 \\

### 2023-09-06 2021-Refinement/paper/SEFM-Extend-RR.tex
version modif.

@@
 %%\usepackage[frenchb]{babel} % optionnel
-\RRNo{7003}
+\RRNo{9517}
 %% \RTNo{0703}
@@
 %% titre francais long
-\RRtitle{Raffinements des Automates Ouverts}
+\RRtitle{Raffinements des automates ouverts}
 %% English title
@@
 Vérifier la correction d'un programme est une tâche complexe souvent réalisée de manière progressive en établissant une relation entre les comportements de deux programmes.
-La relation de simulation, qui met en corespondance   une spécification et une implémentation, ou un programme et sa version raffinée, permet d'assurer la correction.
+La relation de simulation, qui met en correspondance   une spécification et une implémentation, ou un programme et sa version raffinée, permet d'assurer la correction.
 Cet article introduit et discute d'une relation entre des programmes représentés sous la forme d'\emph{automates ouverts}, un modèle comportemental symbolique pour les systèmes de communication.
@@
 %% \RRprojet{Apics}  % cas d'un seul projet
-\RRprojets{LTCI and LIP and KAIROS}
+\RRprojets{CASH and KAIROS}
 %%
@@
 %% \URRennes  % pour ceux qui sont \`a l'ouest 
-%% \URRhoneAlpes % pour ceux qui sont dans les montagnes
+\URRhoneAlpes % pour ceux qui sont dans les montagnes
 %% \URRocq % pour ceux qui sont au centre de la France
 %% \URFuturs % pour ceux qui sont dans le virtuel
-%% \URSophia % pour ceux qui sont au Sud.
+% \URSophia % pour ceux qui sont au Sud.
 %%
@@
 %% \RCRennes % Rennes - Bretagne Atlantique
-\RCSophia % Sophia Antipolis M\'editerran\'ee
+%\RCSophia % Sophia Antipolis M\'editerran\'ee
 
@@
 $A_2\subst{A_3}{k}$),  to prove the theorem it is sufficient to prove that there exists a relation between states of the two OA that satisfies the conditions of  Definition~\ref{Def:OA-Refinement}.
-
-We denote $A_1=  \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}$ and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and $A_3 = \OA{S_3}{s_{03}}{J_3}{V_3}{\sigma_{03}}{T_3}$.
+We denote $A_1=  \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}$, \(A_2 = \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\) and $A_3 = \OA{S_3}{s_{03}}{J_3}{V_3}{\sigma_{03}}{T_3}$.
 The proof requires  to rename the variables of one instance of the two $A_3$ automata to avoid clashes in variable names (this is required by the definition of refinement).
@@
 By using the fact that $\mathcal{R}$ relates initial configurations of  $A_1$ and $A_2$, we have:
-$\mpar{\sigma_{01} \uplus \sigma_{02} \vdash \mathcal{R}\mpar{s_{01}, s_{02}}}$.  
+\[\mpar{\sigma_{01} \uplus \sigma_{02} \vdash \mathcal{R}\mpar{s_{01}, s_{02}}}\]  
 %and based on the  fact that initial states are reachable $\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}$ we have 
@@
 %\mpar{\sigma_{013} \vdash \reach{A_{13}}\mpar{s_{013}}}\]
-
 Considering that initial valuations $\sigma_{03}^1$ and $\sigma_{03}^2$ associate the same values to the ``same'' variables modulo renaming, so the following holds:\\ $\left(\,\,{\displaystyle \bigwedge_\subbox{v_3\in V_3} v^1_3=v^2_3\wedge s^1_3 = s^2_3}\right)\psubst{\sigma_{03}^1 \uplus \sigma_{03}^2 }$.
@@
 \end{enumerate}
-
+\newpage
+\tableofcontents
 \end{document}

### 2023-09-06 2021-Refinement/paper/SEFM-Extend-RR.tex
symbolic

--- 2023-08-30 2021-Refinement/paper/SEFM-Extend-RR.tex
@@
 This form of composition is more complex to handle than top-level interaction usually found in process algebra, as the behaviour of each entity in the system is parameterised both by classical symbolic variables and by process variables.
+
+% symbolic
+Symbolic systems and their bisimulation raises additional challenges~\cite{HENNESSY:1995,henrio:01299562}.
+Reasoning on a symbolic automaton allows one to represent an infinite system in a finite manner, but then the state of the system is not only characterised by an automaton state but also by the value of the different variables representing the system.
+In parameterised systems, it is necessary to guard state  transitions depending on the system state and on the action parameters.
+This is why in previous works and in this article, it we extend the classical form of bisimulation relation: in a symbolic setting a bisimulation relation relates classically states f two systems but it is additionally  parameterised by a formula that must be verified by the state variables.
+This has been introduced in details in previous works~\cite{AMHEEMA:2023,henrio:01299562} and will be recalled briefly in Section~\ref{sec:def}.
 

### 2023-09-06 2021-Refinement/paper/refinementarticleV2.tex
symbolic

@@
 This form of composition is more complex to handle than top-level interaction usually found in process algebra, as the behaviour of each entity in the system is parameterised both by classical symbolic variables and by process variables.
+
+% symbolic
+\LUDO{Symbolic systems and their bisimulation raises additional challenges~\cite{HENNESSY:1995,henrio:01299562}.
+Reasoning on a symbolic automaton allows one to represent an infinite system in a finite manner, but then the state of the system is not only characterised by an automaton state but also by the value of the different variables representing the system.
+In parameterised systems, it is necessary to guard state  transitions depending on the system state and on the action parameters.
+This is why in previous works and in this article, it we extend the classical form of bisimulation relation: in a symbolic setting a bisimulation relation relates classically states f two systems but it is additionally  parameterised by a formula that must be verified by the state variables.
+This has been introduced in details in previous works~\cite{AMHEEMA:2023,henrio:01299562} and will be recalled briefly in Section~\ref{sec:def}.}
 

### 2023-09-06 2021-Refinement/paper/SEFM-Extend-RR.tex

--- 2023-09-06 2021-Refinement/paper/SEFM-Extend-RR.tex
@@
 
+% symbolic
+Symbolic systems and their bisimulation raises additional challenges~\cite{HENNESSY:1995,henrio:01299562}.
+Reasoning on a symbolic automaton allows one to represent an infinite system in a finite manner, but then the state of the system is not only characterised by an automaton state but also by the value of the different variables representing the system.
+In parameterised systems, it is necessary to guard state  transitions depending on the system state and on the action parameters.
+This is why in previous works and in this article, it we extend the classical form of bisimulation relation: in a symbolic setting a bisimulation relation relates classically states f two systems but it is additionally  parameterised by a formula that must be verified by the state variables.
+This has been introduced in details in previous works~\cite{AMHEEMA:2023,henrio:01299562} and will be recalled briefly in Section~\ref{sec:def}.
+
 % why refinement

### 2023-09-07 2021-Refinement/paper/refinementarticleV2.tex
zoom meeting

--- 2023-09-01 2021-Refinement/paper/refinementarticleV2.tex
@@
 
+% symbolic
+Symbolic systems and their bisimulation raises additional challenges~\cite{HENNESSY:1995,henrio:01299562}.
+Reasoning on a symbolic automaton allows one to represent an infinite system in a finite manner, but then the state of the system is not only characterised by an automaton state but also by the value of the different variables representing the system.
+In parameterised systems, it is necessary to guard state  transitions depending on the system state and on the input values.
+This is why in previous works and in this article, it we extend the classical form of bisimulation relation: in a symbolic setting a bisimulation relation relates classically states of two systems but it is additionally  parameterised by a formula that must be verified by the state variables.
+This has been introduced in details in previous works~\cite{AMHEEMA:2023,henrio:01299562} and will be recalled briefly in Section~\ref{sec:def}.
+
 % why refinement
@@
 \subsection{Preliminaries and notations}
-Families of values (equivalent to maps) will be noted \(x_i^{i \in I}\), \(\mset{i \mapsto x_i}{i \in I}\), or \(\mset{i \gets x_i}{i \in I}\), depending on what is more convenient (e.g.
+Countable families of values (equivalent to maps) will be noted \(x_i^{i \in I}\), \(\mset{i \mapsto x_i}{i \in I}\), or \(\mset{i \gets x_i}{i \in I}\), depending on what is more convenient (e.g.
 $i \gets x_i$ is used for maps that are used as substitution).
@@
 
- We suppose given a decidable satisfiability relation on closed formulas, denoted \({\vdash} f\).
+ We suppose given a satisfiability relation on closed formulas, denoted \({\vdash} f\).
 % In practice one of our objective is to be able to use a SMT solver to reason automatically on the properties of open automata, in this case
@@
 
-An \emph{open transition} is a tuple \nmm{\OTg} with \(s, s' \in S\) the source and target states, \(\alpha \in \actions\) the produced action, \(J' \subseteq J\) the holes involved in the transition, \(\beta_j \in \actions\) the actions of the holes, \(g \in \formulas\) the guard and \(\psi: V \to \terms\) the variable assignments.
+An \emph{open transition} is a tuple \nmm{\OTg} with \(s, s' \in S\) the source and target states, \(\alpha \in \actions\) the produced action, \(J' \subseteq J\) the holes involved in the transition, \(g \in \formulas\) the guard and \(\psi: V \to \terms\) the variable  assignments.
+Each \(\beta_j \in \actions\) is an action of the holes $j$,
 To be well-formed, an open transition should use only variables of the automaton and variables appearing in the involved actions, formally: 
@@
 The composition consists of two states (the product of the states of both automata).
-The transitions from one state to another come from  the synchronisation  of the transitions of the encompassing automaton with those of the producer filling the hole $\texttt{P}$.
+The transitions from one state to another come from  the synchronisation  of the transitions of the encompassing automaton with those of the producer filling the hole $\texttt{P}$, this is why there is no more action from hole $P$ in the composed automaton.
 Transitions involving \texttt{Q} remain unchanged.
@@
 Additionally, we say that the relation $ \mathcal{R}$ \emph{relates the initial states} of the automata if: \(\sigma_{01} \uplus \sigma_{02} \vdash  \mathcal{R}\mpar{s_{01}, s_{02}}\).
+We illustrate such a relation over automata with bisimulation relation below.
 
@@
 %\end{minipage}
- such that  $\forall x.\, J'=J_{x}$ and there exists $Pred_{s',t_x}$ such that $(s',t_x|Pred_{s',t_x})\in 
- \mathcal{R}$
+ such that  $\forall x.\, J'=J_{x}$ and there exists $Pred_{s',t_x}$ such that $\mathcal{R}(s',t_x) 
+ $ holds
  and  
@@
 The notion of deadlock should however be specialised to our OA. 
-Indeed, the possible transitions are better characterised by the guards of the outgoing transitions from a given state, rather than the simple existence of a transition.
+Indeed, it is not very useful to check the  existence of a transition, instead it makes more sense to use the guards to check if a transition can be taken.
  We thus define a deadlock reduction criterion based on how the outgoing transitions are guarded.
@@
 Indeed, one can see that  $\mathcal{R}=\{(r_0,s_0) \mapsto \texttt{l}=\texttt{f}, (r_0,s_1) \mapsto \texttt{f}=\texttt{l}+1\% \texttt{N} \}$ is  a  simulation 
-relation. It follows that  \texttt{prod-cons} $\leq$ \texttt{simprod-cons}. \qed
+relation. It follows that  \texttt{simprod-cons} $\leq$ \texttt{prod-cons}. \qed
 \end{example}
@@
 \begin{example} Consider the automata of Examples \ref{Example:fifo-system} and \ref{example:fifo-system-one}.
-As we saw above, \texttt{prod-cons} $\leq$ \texttt{simprod-cons}, therefore \texttt{prod-cons} $\leq_{\{\texttt{P,Q}\}}$ \texttt{simprod-cons}.
+As we saw above, \texttt{simprod-cons} $\leq$ \texttt{prod-cons}, therefore \texttt{prod-cons} $\leq_{\{\texttt{P,Q}\}}$ \texttt{simprod-cons}.
 \end{example}
@@
 Like in the definition of simulation (Definition~\ref{def:HoleEqualSim}) we use guards to ensure that the transition can occur. 
-In general, one would not want to only consider non-blocking composition as it may reveal a bit restrictive, but it is the best necessary condition that can be identified for compositionality of simulation.
+In general, one would not want to only consider non-blocking composition as it may reveal a bit restrictive, but it is the best necessary condition that we could  identify for compositionality of simulation.
 It will be used to prove composition theorems given below.

### 2023-09-07 2021-Refinement/paper/refinementarticleV2.tex
zoom meeting

@@
 An OA \cite{henrio:01299562} is similar to a classical automaton but with variables and holes.
-Variables make automata symbolic and allow them to encode infinite state systems.
+Variables make automata symbolic and allow them to encode infinite-state systems.
 Holes enable the composition of automata: an automaton with a hole is an operator that takes another automaton as parameter and reacts to the actions it emits; the composed automaton is an automaton where the behaviour of one ``process parameter'' %
@@
 
-An \emph{open transition} is a tuple \nmm{\OTg} with \(s, s' \in S\) the source and target states, \(\alpha \in \actions\) the produced action, \(J' \subseteq J\) the holes involved in the transition, \(g \in \formulas\) the guard and \(\psi: V \to \terms\) the variable  assignments.
+An \emph{open transition} is a structure \nmm{\OTg} made of several composing entities, equivalent to a tuple.
+In an open transition \(s, s' \in S\) are the source and target states, \(\alpha \in \actions\) is the resulting action that can be observed from the outside, \(J' \subseteq J\) are the holes involved in the transition, \(g \in \formulas\) is the guard that may constraint the transition, and \(\psi: V \to \terms\) are the variable  assignments that have an effect on the state of the automaton.
 Each \(\beta_j \in \actions\) is an action of the holes $j$,
@@
 \begin{definition}[Out-transition, Transition variables]
-Let \(V\) be the variable names of a considered automaton, \(T\) its transitions and \(r\) one of its states.
-\(\fOT[T]{r} \subset T\) are called the out-transitions of the state \(r\).
+Let $\OAg$ be an automaton and let $r$ be a state in  $S$.
+%Let \(V\) be the set of variable names of a considered automaton, \(T\) the set of transitions and \(r\) one of its states.
+\(\fOT[T]{r} \subset T\) are the transition outgoing from state $r$\footnote{When the set \(T\) is clear from the context, it will be omitted and we will use $\fOT{r}$}.
 %\(\fIT[T]{r} \subset T\) are called the in-transitions of the state \(r\).
-When the set \(T\) is clear from the context, it will be omitted.
 The local variables of a transition \(\fvars{t}\) are all variables appearing in transition \(t\) except the variables of the automaton.
+Outgoing transitions and variables are formally defined as follows.
 %\begin{align*}
@@
          {s_2 \OTarrow {\alpha_{2 x}} s_{2 x}'}
-}^{x \in X}\in \fOT{s_2}.\,~~\\ 
+}^{x \in X}\in \fOT{s_2}.\,~~\\[2pt]
+\mpar{\forall x \in X, J'_{2x} = J'_1 } \nwedge\hfill\\[1pt]
 %\everymath{\displaystyle}\begin{array}{l}
@@
 \mpar{\begin{array}{l}
-			\alpha_{2x} = \alpha_{1} \wedge \bigwedge_\subbox{j \in J} \beta_{2xj} = \beta_{1j} \nwedge\\[12pt]
+			\alpha_{2x} = \alpha_{1} \wedge \bigwedge_\subbox{j \in J'_1} \beta_{2xj} = \beta_{1j} \nwedge\\[12pt]
 			 g_{2x} \wedge\mathcal{R}\mpar{ s'_{1},s'_{2x}}\psubst{\psi_{2x} \uplus \psi_{1}}
@@
 		 V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\\hspace{5em} \mpar{\mathcal{R}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
-			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap H} \beta_{1j} = \beta_{2xj}   \nwedge\\
+			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{1} \cap H} \beta_{1j} = \beta_{2xj}   \nwedge\\
 			 g_{2x} \wedge \mathcal{R}\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}

### 2023-09-07 2021-Refinement/paper/refinementarticleV2.tex
zoom meeting

@@
 The first OA decides when the second can evolve by involving its hole in a transition: the action emitted when \(A_p\) makes a transition is synchronised with the action of the hole \(k\) in transitions of \(A_c\).
+The condition $ \alpha_p = \beta_k$ ensures that the action emitted by the automaton $A_p$ filling the hole is the one expected in the hole $h$ of the open automaton $A_c$.
 
@@
 More formally, for any pair of states $s_1$ and $s_2$  we introduce a criterion of the form:
+\begin{multline*}
+\left(\forall \mpar{s_1, s_2} \!\in\!
+S_1 \!\times\!
+S_2, V_1 \uplus V_2  \vdash \mathcal{R}\mpar{s_1, s_2} \wedge \lnot( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1})\right) \\\implies \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
+\end{multline*}
+
+Which can be rewritten as:
 \[
+\left(
 \forall \mpar{s_1, s_2} \!\in\!
 S_1 \!\times\!
-S_2, V_1 \uplus V_2  \vdash \mathcal{R}\mpar{s_1, s_2} \wedge \lnot( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} )\implies \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
-\]
-
-Which can be rewritten as:
-\[
-\forall \mpar{s_1, s_2} \!\in\!
-S_1 \!\times\!
-S_2, V_1 \uplus V_2  \vdash \mathcal{R}\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
+S_2, V_1 \uplus V_2  \vdash \mathcal{R}\mpar{s_1, s_2}\right) \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
 \]
@@
 In the following definition we add a parameter $H$ which is the set of holes tracked by the simulation relation and adapt the definition by ignoring actions of the holes that are not in $H$.
+\TODO{add comments} we do not have any guarantee on the action of the holes inside $H$.
+The idea is that we will provide composition properties on the h but not outside
+
 \begin{definition}[Hole-tracking simulation]\label{Def:OA-Refinement}
-For two OA\\ \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a simulation of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a relation on configurations $\mathcal{R}: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that:
+For two OA\\ \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a simulation of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a relation on configurations $\mathcal{R}: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that\footnote{Note that the definition below is identical to the hole equal simulation except $\cap H$ is added in a few places.}:
 \item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash \mathcal{R}\mpar{s_{01}, s_{02}}\)

### 2023-09-07 2021-Refinement/paper/refinementarticleV2.tex
exists

@@
   \end{minipage}
-$s$ and $t$ are bisimilar, written $s\sim t$ iff there is a bisimulation relation $\mathcal{R}$ such that  $s ~\mathcal{R}~ t$
+$s$ and $t$ are bisimilar, written $s\sim t$ iff there is a bisimulation relation $\mathcal{R}$ such that  $s ~\mathcal{R}~ t$.
+If only the first one of the two implications above is verified, we say that $s$ simulates $t$ and denote it $s\leq t$.
 \end{definition}
@@
 When dealing with open systems it is common to define simulation in terms of a simulation relation.
-We rely on a classical notion of simulation inspired from~\cite{AMHEEMA:2023}.
+We rely on a classical notion of simulation and perform the same extension as in~\cite{AMHEEMA:2023}, i.e.
+we start from a simulation relation and add holes and symbolic.
 The idea is to consider two configurations related by a relation; if one state can do a transition, then the other can also make this transition.
@@
 %\everymath{\displaystyle}\begin{array}{l}
-V_1 \uplus V_2 \uplus  \fvars{t_1} \vdash \bigsymb{\bigexists} \mpar{\bigcup_x\fvars{t_{2x}}}. \hspace{7cm}
-\\
+V_1 \uplus V_2 \uplus  \fvars{t_1} \vdash 
  \mathcal{R}\mpar{s_1, s_2} \wedge g_1 \implies
@@
 		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\[12pt]
-		\quad \mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H} \nwedge\\[1pt]
+		\quad \mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H} \nwedge\hfill\\[1pt]
 		 V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\\hspace{5em} \mpar{\mathcal{R}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}

### 2023-09-07 2021-Refinement/paper/refinementarticleV2.tex
Open transition notation consistency, reverted affiliation just in case

@@
 Rabéa Ameur-Boulifa\inst{1}\orcidID{0000-0002-2471-8012} \and
-Quentin Corradi\inst{4}\orcidID{0000-0003-4218-3987} \and
+Quentin Corradi\inst{2}\orcidID{0000-0003-4218-3987} \and
 Ludovic Henrio \inst{2}\orcidID{0000-0001-7137-3523} \and
@@
 INRIA Sophia Antipolis M\'edit\'erann\'ee, UCA,  France\\
-\email{first.last@inria.fr}
-\and
-Imperial College London, United Kingdom (previously Universit\'e Lyon)\\
-\email{qc322[at]ic.ac.uk}}
+\email{first.last@inria.fr}}
 %
@@
 
-  \draw (1) edge[align=center] node[below]{\OT{}{}{\alpha(x)}{\{h\mapsto\beta(x)\}}{x<0}{(y\leftarrow -x)}}  (2);
-  \draw (1) edge[align=center] node[above]{\OT{}{}{\alpha(x)}{\{h\mapsto\beta(x)\}}{x\geq 0}{(y\leftarrow x)}} (3);
+  \draw (1) edge[pos=.4] node[below=8pt]{\OTd{\alpha(x)}{h\mapsto\beta(x)}[x<0]{y\leftarrow -x}}  (2);
+  \draw (1) edge[pos=.4] node[above]{\OTd{\alpha(x)}{h\mapsto\beta(x)}[x\geq 0]{y\leftarrow x}} (3);
 \end{tikzpicture}
@@
   \node[state,inner sep=5pt,minimum size=10pt,  right of=1,right=90pt] (2) {$t_2$};
-\draw (1) edge[align=center] node[below]{\OT{}{}{\alpha(x)}{\{h\mapsto\beta(x)\}}{True}{(z\leftarrow x)}}  (2);
-%  \draw (1) edge[align=center] node[above]{\OT{}{}{\alpha(x)}{h\mapsto\beta(x)}{x\geq 0}{y\leftarrow x}} (3);
+\draw (1) edge[align=center] node[below]{\OTd{\alpha(x)}{h\mapsto\beta(x)}{z\leftarrow x}}  (2);
+%  \draw (1) edge[align=center] node[above]{\OTd{\alpha(x)}{h\mapsto\beta(x)}{x\geq 0}{y\leftarrow x}} (3);
 \end{tikzpicture}~

### 2023-09-07 2021-Refinement/paper/refinementarticleV2.tex
More open transition consistency
vdash -> models

@@
 
- We suppose given a satisfiability relation on closed formulas, denoted \({\vdash} f\).
+ We suppose given a satisfiability relation on closed formulas, denoted \({\models} f\).
 % In practice one of our objective is to be able to use a SMT solver to reason automatically on the properties of open automata, in this case
-%\(\vdash\) can hence be interpreted as an indicator of what is given to the SMT; it separates the external logic and the logic on \(\formulas\).
+%\(\models\) can hence be interpreted as an indicator of what is given to the SMT; it separates the external logic and the logic on \(\formulas\).
 We will use two variants of the satisfiability relation:
@@
 \item The satisfiability of a formula \(f \in \formulas\) under some valuation \(\sigma: V \to \values\) is defined as follows:
-\( \sigma \vdash f \iff \vdash \exists \fvars{f\psubst{\sigma}}, f\psubst{\sigma} \)
+\( \sigma \models f \iff \models \exists \fvars{f\psubst{\sigma}}, f\psubst{\sigma} \)
 \item The satisfiability of a formula \(f \in \formulas\) with some variable set \(V\) as context is defined as follows:
-\( V \vdash f \iff  \vdash \forall V, \exists\mpar{\fvars{f} \setminus V}, f \)
+\( V \models f \iff  \models \forall V, \exists\mpar{\fvars{f} \setminus V}, f \)
 \end{itemize}
@@
 In other words, to each pair of states is attached a boolean formula that may refer to the  variables of each of the two OA, stating whether the two states are related or not.
-Additionally, we say that the relation $ \mathcal{R}$ \emph{relates the initial states} of the automata if: \(\sigma_{01} \uplus \sigma_{02} \vdash  \mathcal{R}\mpar{s_{01}, s_{02}}\).
+Additionally, we say that the relation $ \mathcal{R}$ \emph{relates the initial states} of the automata if: \(\sigma_{01} \uplus \sigma_{02} \models  \mathcal{R}\mpar{s_{01}, s_{02}}\).
 We illustrate such a relation over automata with bisimulation relation below.
@@
 %\TODO{I do not think we reason on configurations for the moment, if we want to, we should introduce this:}
-%Two configurations \(\mpar{s_1, \sigma_1} \in S_1 \times\mpar{V_1 \to \values}, \mpar{s_2, \sigma_2} \in S_2 \times \mpar{V_2 \to \values}\) are related iff \(\sigma_1 \uplus \sigma_2 \vdash R\mpar{s_1, s_2}\).
+%Two configurations \(\mpar{s_1, \sigma_1} \in S_1 \times\mpar{V_1 \to \values}, \mpar{s_2, \sigma_2} \in S_2 \times \mpar{V_2 \to \values}\) are related iff \(\sigma_1 \uplus \sigma_2 \models R\mpar{s_1, s_2}\).
 
@@
 
-  \draw (1) edge[pos=.4] node[below=8pt]{\OTd{\alpha(x)}{h\mapsto\beta(x)}[x<0]{y\leftarrow -x}}  (2);
+  \draw (1) edge[pos=.4] node[below=6pt]{\OTd{\alpha(x)}{h\mapsto\beta(x)}[x<0]{y\leftarrow -x}}  (2);
   \draw (1) edge[pos=.4] node[above]{\OTd{\alpha(x)}{h\mapsto\beta(x)}[x\geq 0]{y\leftarrow x}} (3);
@@
 For any OA \(A = \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is any predicate on states that is valid on initial state, and preserved across transitions:
-\[\sigma_0 \vdash \reach{A}\mpar{s_0}\quad\land\quad\forall t = \OTg \in T, \fvars{t} \vdash \left(\reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}\right)\]
+\[\sigma_0 \models \reach{A}\mpar{s_0}\quad\land\quad\forall t = \OTg \in T, \fvars{t} \models \left(\reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}\right)\]
 \end{definition}
@@
 % \forall \mpar{s_1, s_2} \in S_1 \times S_2,
-% \\ V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
+% \\ V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \models \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
 %\end{multline*}
@@
 %The composition \(A_0\mdbrk{j_i \mapsto A_i \middle| 1 \leq i \leq n}\) is non-blocking if   \(A \) has a reachability predicate such that, for each reachable configuration, if there is a possible transition in \(A_0\) then there is a possible transition in \(A\):
-%\[ \forall s = \mpar{s_0, s_1,..,s_n} \in S, V \uplus \biguplus_\subbox{t_0 \in \fOT{s_0}} \fvars{t_0} \vdash \left(\reach{A}\mpar{s} \wedge \bigvee_\subbox{t_0 \in \fOT{s_0}} \fguard{t_0} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \right)\]
+%\[ \forall s = \mpar{s_0, s_1,..,s_n} \in S, V \uplus \biguplus_\subbox{t_0 \in \fOT{s_0}} \fvars{t_0} \models \left(\reach{A}\mpar{s} \wedge \bigvee_\subbox{t_0 \in \fOT{s_0}} \fguard{t_0} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \right)\]
 %\end{definition}
@@
 S_1 \!\times\!
-S_2, V_1 \uplus V_2  \vdash \mathcal{R}\mpar{s_1, s_2} \wedge \lnot( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1})\right) \\\implies \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
+S_2, V_1 \uplus V_2  \models \mathcal{R}\mpar{s_1, s_2} \wedge \lnot( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1})\right) \\\implies \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
 \end{multline*}
@@
 S_1 \!\times\!
-S_2, V_1 \uplus V_2  \vdash \mathcal{R}\mpar{s_1, s_2}\right) \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
+S_2, V_1 \uplus V_2  \models \mathcal{R}\mpar{s_1, s_2}\right) \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
 \]
@@
 %\begin{multline*}
-%\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_2} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\  V_1 \uplus V_2 \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \implies  R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}\\
+%\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_2} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\  V_1 \uplus V_2 \uplus \fvars{t_1} \uplus \fvars{t_2} \models \hspace{6cm}\\  R\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 \wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} \implies  R\mpar{s'_1, s'_2}\psubst{\psi_1 \uplus \psi_2}\\
 %\end{multline*}
@@
 \(A_1 = \OA{S_1}{s_{01}}{V_1}{\sigma_{01}}{J}{T_1}\) and \(A_2 = \OA{S_2}{s_{02}}{V_2}{\sigma_{02}}{J}{T_2}\), the relation on configurations \(\mathcal{R}: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $A_1$ to $A_2$ if the following conditions hold :
-\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash \mathcal{R}\mpar{s_{01}, s_{02}}\)
+\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \models \mathcal{R}\mpar{s_{01}, s_{02}}\)
 \item[(2)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)\vspace{-8pt}
 \noindent\begin{multline*}
- \bigsymb{\forall} {t_1} = \openrule
-         {
-           \beta_{1 j}^{j\in J'_{1}}, g_1,\psi_1}
-         {s_1 \OTarrow {\alpha_1} s_1'} \in \fOT{s_1} .\,~~
+ \bigsymb{\forall} {t_1} = \OTx{1}{}{1}{1} \in \fOT{s_1} .\,~~
 \bigsymb{\bigexists} 
-\mpar{t_{2x} \!=\! \openrule
-         {
-           \beta_{2 x j}^{j\in J'_{2x}}, g_{2 x},\psi_{2 x}}
-         {s_2 \OTarrow {\alpha_{2 x}} s_{2 x}'}
-}^{x \in X}\in \fOT{s_2}.\,~~\\[2pt]
+\mpar{t_{2x} \!=\! \OTx{2}{x}{2x}{2x}}^{x \in X}\in \fOT{s_2}.\,~~\\[2pt]
 \mpar{\forall x \in X, J'_{2x} = J'_1 } \nwedge\hfill\\[1pt]
 %\everymath{\displaystyle}\begin{array}{l}
-V_1 \uplus V_2 \uplus  \fvars{t_1} \vdash 
+V_1 \uplus V_2 \uplus  \fvars{t_1} \models 
  \mathcal{R}\mpar{s_1, s_2} \wedge g_1 \implies
@@
 S_1 \!\times\!
-S_2, V_1 \uplus V_2  \!\vdash\!
+S_2, V_1 \uplus V_2  \!\models\!
 \mathcal{R}\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
@@
 For two OA\\ \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a simulation of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a relation on configurations $\mathcal{R}: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that\footnote{Note that the definition below is identical to the hole equal simulation except $\cap H$ is added in a few places.}:
-\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash \mathcal{R}\mpar{s_{01}, s_{02}}\)
+\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \models \mathcal{R}\mpar{s_{01}, s_{02}}\)
 \item[(2)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)
@@
 		\quad \mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H} \nwedge\hfill\\[1pt]
-		 V_1 \uplus V_2 \uplus \fvars{t_1} \vdash\\\hspace{5em} \mpar{\mathcal{R}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
+		 V_1 \uplus V_2 \uplus \fvars{t_1} \models\\\hspace{5em} \mpar{\mathcal{R}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
 			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{1} \cap H} \beta_{1j} = \beta_{2xj}   \nwedge\\
@@
 S_1 \!\times\!
-S_2, V_1 \uplus V_2  \vdash \mathcal{R}\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
+S_2, V_1 \uplus V_2  \models \mathcal{R}\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
 \]
@@
 \begin{multline*}
- \forall \mpar{s_1, s_2} \in S_1 \times S_2,\\ V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
+ \forall \mpar{s_1, s_2} \in S_1 \times S_2,\\ V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \models \left(R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \right)
 \end{multline*}
@@
 %For any open automata \(A = \OAg\), a reachability predicate \(\reach{A}: S \to \rformulas[V]\) is any predicate on states that is valid on initial state, and preserved across transitions:
-%\[\sigma_0 \vdash \reach{A}\mpar{s_0}\quad\land\quad\forall t = \OTg \in T, \fvars{t} \vdash \left(\reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}\right)\]
+%\[\sigma_0 \models \reach{A}\mpar{s_0}\quad\land\quad\forall t = \OTg \in T, \fvars{t} \models \left(\reach{A}\mpar{s} \wedge g \implies \reach{A}\mpar{s'}\psubst{\psi}\right)\]
 %\end{definition}
@@
 %\begin{multline*}
-% \forall s = \mpar{s_0, s_1,..,s_n} \in S, V \uplus \biguplus_\subbox{t_0 \in \fOT{s_0}} \fvars{t_0} \vdash \\ \left(\reach{A}\mpar{s} \wedge \bigvee_\subbox{t_0 \in \fOT{s_0}} \fguard{t_0} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \right)
+% \forall s = \mpar{s_0, s_1,..,s_n} \in S, V \uplus \biguplus_\subbox{t_0 \in \fOT{s_0}} \fvars{t_0} \models \\ \left(\reach{A}\mpar{s} \wedge \bigvee_\subbox{t_0 \in \fOT{s_0}} \fguard{t_0} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \right)
 %\end{multline*}
@@
 %\begin{multline*}
-\[ \forall s = \mpar{s_1, s_2} \in S, V \uplus \biguplus_\subbox{t \in \fOT{s_1}} \fvars{t} \vdash  \left(\reach{A}\mpar{s} \wedge \bigvee_\subbox{t \in \fOT{s_1}} \fguard{t} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \right)
+\[ \forall s = \mpar{s_1, s_2} \in S, V \uplus \biguplus_\subbox{t \in \fOT{s_1}} \fvars{t} \models  \left(\reach{A}\mpar{s} \wedge \bigvee_\subbox{t \in \fOT{s_1}} \fguard{t} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \right)
 \]

### 2023-09-07 2021-Refinement/paper/refinementarticleV2.tex
Red arrow for open transition
Deadlock reduction parenthesis
More todos

--- 2023-09-07 2021-Refinement/paper/refinementarticleV2.tex
@@
 This is why in previous works and in this article, it we extend the classical form of bisimulation relation: in a symbolic setting a bisimulation relation relates classically states of two systems but it is additionally  parameterised by a formula that must be verified by the state variables.
-This has been introduced in details in previous works~\cite{AMHEEMA:2023,henrio:01299562} and will be recalled briefly in Section~\ref{sec:def}.
+This has been introduced in details in previous works~\cite{AMHEEMA:2023} and will be recalled briefly in Section~\ref{sec:def}.
+We have shown in previous works that open symbolic systems are particularly convenient to model process algebra operators and open component systems with infinite behaviour~\cite{AMHEEMA:2023,henrio:01299562}.
 

### 2023-09-07 2021-Refinement/paper/refinementarticleV2.tex

--- 2023-09-07 2021-Refinement/paper/refinementarticleV2.tex
@@
 $
-     \OTbase{s \xrightarrow{\alpha} s'}
+     \OTbase{s \OTarrow{\alpha} s'}
          {
@@
 %    \left( fresh \ \set{\alpha_i}, \set{b_j}, v_x.\ \
-    \OTbase{t \xrightarrow{\alpha_x} t_x}
+    \OTbase{t \OTarrow{\alpha_x} t_x}
          {
@@
 \begin{multline*}
-\left(\forall \mpar{s_1, s_2} \!\in\!
-S_1 \!\times\!
-S_2, V_1 \uplus V_2  \models \mathcal{R}\mpar{s_1, s_2} \wedge \lnot( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1})\right) \\\implies \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
+\forall \mpar{s_1, s_2} \in S_1 \times S_2, \\
+	V_1 \uplus V_2 \models \biggl( \mathcal{R}\mpar{s_1, s_2} \wedge \lnot \Bigl( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} \Bigr) \implies \lnot \Bigl( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \Bigr) \biggr)
 \end{multline*}
@@
 \[
-\left(
-\forall \mpar{s_1, s_2} \!\in\!
-S_1 \!\times\!
-S_2, V_1 \uplus V_2  \models \mathcal{R}\mpar{s_1, s_2}\right) \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
+\forall \mpar{s_1, s_2} \!\in\! S_1 \!\times\! S_2, V_1 \uplus V_2
+	\models\!
+\biggl(\!
+\mathcal{R}\mpar{s_1, s_2} \!\implies\!
+\Bigl(\!\!
+\bigvee_\subbox{t_1 \in \fOT{s_1}}\!
+\fguard{t_1} \Bigr) \lor \lnot \Bigl(\!\!
+\bigvee_\subbox{t_2 \in \fOT{s_2}}\!
+\fguard{t_2} \Bigr) \!\biggr)
 \]
@@
 \[
-\forall \mpar{s_1, s_2} \!\in\!
-S_1 \!\times\!
-S_2, V_1 \uplus V_2  \!\models\!
-\mathcal{R}\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
+\forall \mpar{s_1, s_2} \!\in\! S_1 \!\times\! S_2, V_1 \uplus V_2
+	\models\!
+\biggl(\!
+\mathcal{R}\mpar{s_1, s_2} \!\implies\!
+\Bigl(\!\!
+\bigvee_\subbox{t_1 \in \fOT{s_1}}\!
+\fguard{t_1} \Bigr) \lor \lnot \Bigl(\!\!
+\bigvee_\subbox{t_2 \in \fOT{s_2}}\!
+\fguard{t_2} \Bigr) \!\biggr)
 \]
@@
 \[
-\forall \mpar{s_1, s_2} \!\in\!
-S_1 \!\times\!
-S_2, V_1 \uplus V_2  \models \mathcal{R}\mpar{s_1, s_2} \implies( \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1} ) \lor¢ \lnot( \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2}  )
+\forall \mpar{s_1, s_2} \!\in\! S_1 \!\times\! S_2, V_1 \uplus V_2
+	\models\!
+\biggl(\!
+\mathcal{R}\mpar{s_1, s_2} \!\implies\!
+\Bigl(\!\!
+\bigvee_\subbox{t_1 \in \fOT{s_1}}\!
+\fguard{t_1} \Bigr) \lor \lnot \Bigl(\!\!
+\bigvee_\subbox{t_2 \in \fOT{s_2}}\!
+\fguard{t_2} \Bigr) \!\biggr)
 \]
@@
 %\begin{multline*}
-\[ \forall s = \mpar{s_1, s_2} \in S, V \uplus \biguplus_\subbox{t \in \fOT{s_1}} \fvars{t} \models  \left(\reach{A}\mpar{s} \wedge \bigvee_\subbox{t \in \fOT{s_1}} \fguard{t} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \right)
+\[ \forall s = \mpar{s_1, s_2} \in S, V \uplus \biguplus_\subbox{t \in \fOT{s_1}} \fvars{t} \models  \biggl(\reach{A}\mpar{s} \wedge \bigvee_\subbox{t \in \fOT{s_1}} \fguard{t} \implies \bigvee_\subbox{t \in \fOT{s}} \fguard{t} \biggr)
 \]

### 2023-09-07 2021-Refinement/paper/refinementarticleV2.tex
rephrase symbolic

@@
 We informally explain here the symbolic nature of the bisimulation for OA and the related complexity of its definition.
-\RAB{The notion of symbolic bisimulation, as it was introduced in \cite{HENNESSY:1995}, is aimed at computing bisimulation of value-passing processes.
-The class of processes manipulating and exchanging with the environment data, where the values are from possibly infinite domain.}
+The notion of symbolic bisimulation, as it was introduced in \cite{HENNESSY:1995}, is aimed at computing bisimulation of value-passing systems, i.e.
+systems made of processes exchanging data with their environment and between processes, where data are values from a possibly infinite domain.
  The presence of holes in fact raises no strong difficulty but the variables must be handled carefully.

### 2023-09-07 2021-Refinement/paper/refinementarticleV2.tex
more comments, main things done

@@
 The transitions from one state to another come from  the synchronisation  of the transitions of the encompassing automaton with those of the producer filling the hole $\texttt{P}$, this is why there is no more action from hole $P$ in the composed automaton.
-Transitions involving \texttt{Q} remain unchanged.
+Only elements related to the hole $P$ are changed and in particular, transitions involving \texttt{Q} remain unchanged.
 \qed
@@
    \includegraphics[width=.99\textwidth]{Figures/compos-FIFO-Pro.pdf}
-   \caption{OA for \texttt{prod-cons}[\texttt{P}/\texttt{producer}]. 
+   \caption{OA for filling the hole $\texttt{P}$ in \texttt{prod-cons}: \texttt{prod-cons}[\texttt{P}/\texttt{producer}]. 
    \label{Fig:ComposeOA}} 
@@
 The third condition ensures that  simulation  prevents the introduction of deadlocks.
+\LUDO{Similarly to bisimulation, the second condition states that, for any transition of the simulating automaton $A_1$, it corresponds to a transition of the automaton $A_2$ that does the same thing and ends up in a similar state.
+However a family is needed in $A_2$ because of the symbolic nature of transitions, and because depending on the values of the variables, $t_1$ may correspond to different transitions in $A_2$.}
 Our definition captures a simple simulation for OA with the same holes that is more expressive than a strict simulation since it matches a transition with a family of transitions. 
@@
 In the following definition we add a parameter $H$ which is the set of holes tracked by the simulation relation and adapt the definition by ignoring actions of the holes that are not in $H$.
-\TODO{add comments} we do not have any guarantee on the action of the holes inside $H$.
-The idea is that we will provide composition properties on the h but not outside
+\LUDO{
+Consequently, there is no guarantee related to the actions of the holes outside $H$.
+We provide compositionality properties when plugging an automaton inside a hole in $H$ but cannot state anything when plugging an automaton outside $H$.
+The principle is that any property concerning holes that are not in $H$ should be proven specifically for the considered automaton or the considered composition of automata.
+}
 
@@
 \end{property}
+\LUDO{
+In particular if an OA has no holes, the two definitions are equivalent and result in a  ``symbolic simulation'', if additionally there is no variable in the OA, we obtain the classical simulation of process algebra theory.}
+
 \begin{example} Consider the automata of Examples \ref{Example:fifo-system} and \ref{example:fifo-system-one}.

### 2023-09-08 2021-Refinement/paper/refinementarticleV2.tex
corrections...

@@
  of the main automaton has been provided.
-Due to their the generic nature, the notion of OA model is quite abstract but we already illustrated previously how to derive OAs for process algebra operators~\cite{henrio:01299562} or for component systems~\cite{AMHEEMA:2023,ameurboulifa:01526055}.
+Due to their generic nature, the notion of OA model is quite abstract but we already illustrated previously how to derive OAs for process algebra operators~\cite{henrio:01299562} or for component systems~\cite{AMHEEMA:2023,ameurboulifa:01526055}.
 
@@
 The first OA decides when the second can evolve by involving its hole in a transition: the action emitted when \(A_p\) makes a transition is synchronised with the action of the hole \(k\) in transitions of \(A_c\).
-The condition $ \alpha_p = \beta_k$ ensures that the action emitted by the automaton $A_p$ filling the hole is the one expected in the hole $h$ of the open automaton $A_c$.
+The condition $ \alpha_p = \beta_k$ ensures that the action emitted by the automaton $A_p$ filling the hole is the one expected in the hole $k$ of the open automaton $A_c$.
 
@@
 The composition consists of two states (the product of the states of both automata).
-The transitions from one state to another come from  the synchronisation  of the transitions of the encompassing automaton with those of the producer filling the hole $\texttt{P}$, this is why there is no more action from hole $P$ in the composed automaton.
-Only elements related to the hole $P$ are changed and in particular, transitions involving \texttt{Q} remain unchanged.
+The transitions from one state to another come from  the synchronisation  of the transitions of the encompassing automaton with those of the producer filling the hole $\texttt{P}$, this is why there is no more action from hole $\texttt{P}$ in the composed automaton.
+Only elements related to the hole $\texttt{P}$ are changed and in particular, transitions involving \texttt{Q} remain unchanged.
 \qed
@@
 %\end{minipage}
- such that  $\forall x.\, J'=J_{x}$ and there exists $Pred_{s',t_x}$ such that $\mathcal{R}(s',t_x) 
- $ holds
+ such that  $\forall x.\, J'=J_{x}$ and there exists \hl{ $Pred_{s',t_x}$ such that} $\mathcal{R}(s',t_x)  
+ $ holds \RAB{On n'a pas  de Pred dans la def}
  and  
@@
      \land \alpha\!=\!\alpha_x \land  
-     \mathcal{R}\left(s',t_x{\psi_{OT}\!\uplus\!\psi_{OT_x}}\right)\right)}
+     \mathcal{R}\left(s',t_x\right)\psubst{\psi_{OT}\!\uplus\!\psi_{OT_x}}\right)}
 \end{multline*}
@@
 \begin{definition}[Hole-tracking simulation]\label{Def:OA-Refinement}
-For two OA\\ \(A_1 \defobject \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 \defobject \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a simulation of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a relation on configurations $\mathcal{R}: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that\footnote{Note that the definition below is identical to the hole equal simulation except $\cap H$ is added in a few places.}:
+For two OA\\ \(A_1 = \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 = \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a simulation of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a relation on configurations $\mathcal{R}: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that\footnote{Note that the definition below is identical to the hole equal simulation except $\cap H$ is added in a few places.}:
 \item[(1)] \(\sigma_{01} \uplus \sigma_{02} \models \mathcal{R}\mpar{s_{01}, s_{02}}\)
@@
 		\bigsymb{\forall} \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{\OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\[12pt]
-		\quad \mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H} \nwedge\hfill\\[1pt]
+		 \mpar{\forall x \in X, J'_{2x} \cap H = J'_1 \cap H} \nwedge\hfill\\[1pt]
 		 V_1 \uplus V_2 \uplus \fvars{t_1} \models\\\hspace{5em} \mpar{\mathcal{R}\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
@@
 \LUDO{
-In particular if an OA has no holes, the two definitions are equivalent and result in a  ``symbolic simulation'', if additionally there is no variable in the OA, we obtain the classical simulation of process algebra theory.}
+In particular, if an OA has no holes, the two definitions are equivalent and result in a  ``symbolic simulation'', if additionally there is no variable in the OA, we obtain the classical simulation of process algebra theory.}
 
@@
 \begin{definition}[Non-blocking composition] \label{Def:Non-block}
-Consider two OA:\\ \(A_1 \defobject \OAg[1]\) and \( A_2 \defobject \OAg[2]\).
+Consider two OA:\\ \(A_1 = \OAg[1]\) and \( A_2 = \OAg[2]\).
 Let $A$ be the OA resulting from the composition \(A = A_1\subst{A_2}{k}= \OAg\). 
@@
 More precisely, we define a relation of the following form:
-  \[\mathcal{R}_{13}(s_1,s_3)=\bigvee_{s_2\in S_2}\mpar{\mathcal{R}_{12}(s_1,s_2) \land \mathcal{R}_{23}(s_2,s_3) } \]
+  \[\mathcal{R}_{13}(s_1,s_3)=\bigvee_{s_2\in S_2}\left(\mathcal{R}_{12}(s_1,s_2) \land \mathcal{R}_{23}(s_2,s_3) \right) \]
 We then prove that this relation  is a simulation, according to Definition~\ref{Def:OA-Refinement}.
@@
 If the hole $k$ is involved the considered relation  implies that valuations in $A_3$ are equal (i.e., the value for each variable are the same in both valuations), after a transition we should obtain ``equal'' valuations because post-conditions are deterministic.
+\RAB{The requirement $A_1\subst{A_3}{k}$ ensures  compatibility with deadlock reduction, i.e., it ensures that deadlocks in the refined model  are not introduced through composition.}
 \end{proofsketch}

### 2023-09-08 2021-Refinement/paper/refinementarticleV2.tex
zoom meeting

@@
 
-\keywords{Labelled transition systems   \and Simulation \and Refinement \and Composition.}
+\keywords{Labelled transition systems   \and Simulation  \and Composition.}
 \end{abstract}
@@
 We will use two variants of the satisfiability relation:
-\begin{itemize}
+\begin{compactitem}
 \item The satisfiability of a formula \(f \in \formulas\) under some valuation \(\sigma: V \to \values\) is defined as follows:
@@
 \( V \models f \iff  \models \forall V, \exists\mpar{\fvars{f} \setminus V}, f \)
-\end{itemize}
+\end{compactitem}
 
@@
 \end{property}
-\LUDO{
-In particular, if an OA has no holes, the two definitions are equivalent and result in a  ``symbolic simulation'', if additionally there is no variable in the OA, we obtain the classical simulation of process algebra theory.}
+
+In particular, if an OA has no hole, the two definitions are equivalent and result in a  ``symbolic simulation'', if additionally there is no variable in the OA, this corresponds to  classical simulation.
 
@@
 If the hole $k$ is involved the considered relation  implies that valuations in $A_3$ are equal (i.e., the value for each variable are the same in both valuations), after a transition we should obtain ``equal'' valuations because post-conditions are deterministic.
-\RAB{The requirement $A_1\subst{A_3}{k}$ ensures  compatibility with deadlock reduction, i.e., it ensures that deadlocks in the refined model  are not introduced through composition.}
+The requirement ``$A_1\subst{A_3}{k}$ is non-blocking'' ensures the deadlock reduction property holds.
+More precisely, if $A_1\subst{A_3}{k}$ is stuck, then $A_1$ is stuck, and thus $A_1\subst{A_2}{k}$ is also stuck.
 \end{proofsketch}

### 2023-09-08 2021-Refinement/paper/refinementarticleV2.tex
remove highlight + minors errors

@@
 %\end{minipage}
- such that  $\forall x.\, J'=J_{x}$ and there exists \hl{ $Pred_{s',t_x}$ such that} $\mathcal{R}(s',t_x)  
- $ holds \RAB{On n'a pas  de Pred dans la def}
- and  
+ such that the following  holds
 \begin{multline*}
@@
 When dealing with open systems it is common to define simulation in terms of a simulation relation.
-We rely on a classical notion of simulation and perform the same extension as in~\cite{AMHEEMA:2023}, i.e.
-we start from a simulation relation and add holes and symbolic.
+We rely on a classical notion of simulation and perform the same extension as in~\cite{AMHEEMA:2023}, i.e., we start from a simulation relation and add holes and symbolic.
 The idea is to consider two configurations related by a relation; if one state can do a transition, then the other can also make this transition.
@@
 The third condition ensures that  simulation  prevents the introduction of deadlocks.
-\LUDO{Similarly to bisimulation, the second condition states that, for any transition of the simulating automaton $A_1$, it corresponds to a transition of the automaton $A_2$ that does the same thing and ends up in a similar state.
-However a family is needed in $A_2$ because of the symbolic nature of transitions, and because depending on the values of the variables, $t_1$ may correspond to different transitions in $A_2$.}
+Similarly to bisimulation, the second condition states that, for any transition of the simulating automaton $A_1$, it corresponds to a transition of the automaton $A_2$ that does the same thing and ends up in a similar state.
+However a family is needed in $A_2$ because of the symbolic nature of transitions, and because depending on the values of the variables, $t_1$ may correspond to different transitions in $A_2$.
 Our definition captures a simple simulation for OA with the same holes that is more expressive than a strict simulation since it matches a transition with a family of transitions. 
@@
 In the following definition we add a parameter $H$ which is the set of holes tracked by the simulation relation and adapt the definition by ignoring actions of the holes that are not in $H$.
-\LUDO{
+
 Consequently, there is no guarantee related to the actions of the holes outside $H$.
@@
 The principle is that any property concerning holes that are not in $H$ should be proven specifically for the considered automaton or the considered composition of automata.
-}
 
 \begin{definition}[Hole-tracking simulation]\label{Def:OA-Refinement}
-For two OA\\ \(A_1 = \OA{S_1}{s_{01}}{J_1}{V_1}{\sigma_{01}}{T_1}\) and \(A_2 = \OA{S_2}{s_{02}}{J_2}{V_2}{\sigma_{02}}{T_2}\), \(A_1\) is a simulation of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a relation on configurations $\mathcal{R}: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that\footnote{Note that the definition below is identical to the hole equal simulation except $\cap H$ is added in a few places.}:
+For two OA\\ \(A_1 = \OA{S_1}{s_{01}}{V_1}{\sigma_{01}}{J_1}{T_1}\) and \(A_2 = \OA{S_2}{s_{02}}{V_2}{\sigma_{02}}{J_2}{T_2}\), \(A_1\) is a simulation of \(A_2\) tracking holes \(H\), noted \(\wrel{A_1}{A_2}{H}\), with \(H \subseteq J_1 \cap J_2\), if there is a relation on configurations $\mathcal{R}: \mpar{S_1 \times S_2} \to \rformulas[V_1 \uplus V_2]$ such that\footnote{Note that the definition below is identical to the hole equal simulation except $\cap H$ is added in a few places.}:
 \item[(1)] \(\sigma_{01} \uplus \sigma_{02} \models \mathcal{R}\mpar{s_{01}, s_{02}}\)

### 2023-09-26 SujetStage/2022-pNetsubjectM2.tex
open automaton + session types

@@
 The composition of open automata refers to filling holes, it requires to check the compatibility of their sorts.
-Nowadays, we simply verify the compatibility of two automata to be composed based on   action labels and  arity.
+Nowadays, we simply verify the compatibility of two automata to be composed based on   action labels and  arity (comparing actions exposed by one LTS with actions expected to fill the hole).
 But,
- we are interested in enriching holes with description of behaviours to give them enough power and enable us to check equivalences for these open systems. The description will characterise all the
-interactions and the series of inputs and outputs of data exchanged between the automata and its surroundings.
+ we are interested in enriching holes with description of behaviours; this description should look like a communication protocol.
 Precisely, the theory of session types and behavioural types  \cite{Fantechi:MLTCDP2019} are intended  to describe dynamic aspects of the behaviour of processes.
@@
 
-The main objective of the internship is to deal with the characterization of interactions  of open automaton with its environment. These interactions can be characterised as behavioural types.
+The main objective of the internship is to deal with the characterization of interactions  of an automaton with its environment. These interactions can be characterised as behavioural types.
 More specifically, the internship would follow the following steps:
 \begin{itemize}
-\item Familiarization with technical material: the semantics of  open automata and the notion behavioural types \cite{Hans:2016} that allows to describe the dynamic aspects of processes.
+\item Familiarization with technical material: the semantics of  open automata and the notion behavioural types \cite{Hans:2016} that allows the description of the dynamic aspects of processes.
 In particular the notion of session types that focus on process interactions should be studied.
@@
 
-\item Application to the proof of absence of deadlock upon composition.
+\item Prove absence of deadlock upon composition.
 
-\item  We additionally have defined a notion of bisimulation between open automata.
+\item  We  have defined a notion of bisimulation between open automata. 
 One additional objective of the internship could be to prove that behavioural types behave well relatively to bisimilarity.
@@
 
-The internship can be tackled only theoretically on paper, or formalised in an interactive theorem prover, or integrated with existing tools for open automata bisimilarity (based on SMT solvers).
+The internship can be tackled only theoretically on paper, or formalised in an interactive theorem prover, or integrated with existing tools for open automata based on SMT solving.
 

### 2023-09-26 SujetStage/2022-pNetsubjectM2.tex
biblio

@@
 \bibitem{henrio:Forte2016}
-Henrio, L., Madelaine, E., Zhang, M.:
+Ludovic Henrio, Eric Madelaine, Min Zhang:
 \newblock {A Theory for the Composition of Concurrent Processes}.
@@
 \bibitem{hou:hal-02406098}
-Hou, Z., Madelaine, E.:
+Zechen Hou,  Eric  Madelaine:
 \newblock {Symbolic Bisimulation for Open and Parameterized Systems}.
@@
 \bibitem{arxiv-weakbisim}
-Rabéa Ameur-Boulifa and Ludovic Henrio and Eric Madelaine:
+Rabéa Ameur-Boulifa, Ludovic Henrio, Eric Madelaine:
 \newblock {Compositional equivalences based on Open pNets}.
-\newblock arXiv {2007.10770} (2021).
- \newblock \url{https://arxiv.org/abs/2007.10770}
+\newblock Journal of Logical and Algebraic Methods in Programming, 2022, 131, p.100842..
+ \newblock \url{https://hal.science/hal-03894031}
 \end{thebibliography}
